### 2016-08-09 Ben_Manuscripts/Paper1/Outline.tex
Create Outline.tex

\documentclass{article}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia, Michael R. Shirts, Douglas L. Gin, Richard D. Noble}
\begin{document}
\bibliographystyle{ieeetr}
\maketitle
\section{Introduction}

Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
\begin{itemize}
	\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
	\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
	\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
\end{itemize}

Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
\begin{itemize}
	\item Leading technologies and their limitations:
	\begin{itemize}
		\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
		\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
		\item Zeolites - Good rejections/selectivities, but low flux and high cost of manufacturing. Generally limited to applications needing thermal/chemical resistance
	\end{itemize}
\end{itemize}

Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which may be feasible for large scale production.
\begin{itemize}
	\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
	\item My monomer forms HII phase consisting of vertically aligned, monodisperse, straight pores in a hexagonal array
	\item Hydrophilic regions point towards pore centers
	\item Until recently, they could not be aligned - hindered progress
	\item Talk about Yale alignment techniques
	\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
\end{itemize}

A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
\begin{itemize}
	\item HII phase studies currently limited mostly to one monomer with minor variations
	\item Current optimization efforts performed through trial and error
	\item Macroscopic models are the only source of predictive modeling
	\item An atomistic understanding of the mechanism of solute transport can identify
	performance bottle necks and direct design of future monomers/membranes
	\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
	\begin{itemize}
		\item This could change how one thinks about molecules diffusing through membrane
		\item Could also be a difference between lyotropic and thermotropic phases
	\end{itemize}
	\item Will we observe Donnan exclusion or some variation on it at the pore entrance
	\item What are the relative weights of steric and electrical effects that deterimine selectivity -- is there an optimal balance 
	\item How many monomers are in a layer?
	\item What is the equilibrium water content in lyotropic phase?
	\item We can vary the following to make predictions about new systems:
	\begin{itemize}
		\item Liquid crystal used - or a mixture of different liquid crystals
		\item Minor structural variations (e.g. 7, 8, , 9, 10, 11 ... CH2's in the tails)
		\item Counterion -- Size/valence of counterion
		\item Functional head groups
	\end{itemize}
	\item How does varying these things effect pore separation, pore size, phase stability, and transport and why are these effects observed 
\end{itemize}

A physically accurate molecular model with easily modified structural features will launch a new phase of research into directing design of an optimal LLC membrane.
\begin{itemize}
	\item The paper will illustrate the development of a predictive molecular model
	\item Measurements made to validate model
	\item Observations of transport mechanism
	\item The model is consistent with experiments and ready to extend to other systems
\end{itemize}

\section{System Setup}

HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16. All molecular dynamics simulations were run using Gromacs version 5.1.2.

The most suitable monomer structural configuration was decided by applying a simulated annealing process to the parameterized monomer. 
\begin{itemize}
	\item Initially parameterized monomer gives unfavorable structure
	\item Structure cooled from 1000 to 50 K over 10 nanoseconds
	\item Result not global minimum but close enough for structure building
	\item Multiple configurations saved from annealing trajectory to prove independence of starting config
\end{itemize}

The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable simulation length. 
\begin{itemize}
	\item Work done that shows coarse grain model self assembly in ~1000 ns
	\item Attempts with HII system not fruitful
	\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
	\item Code has adjustable parameters: Pore-to-Pore distance, pore radius, number of monomer layers (justification for parameters chosen in following paragraphs)
	\item This is the thermotropic phase, information used depends on thermotropic experimental data
\end{itemize}

After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
\begin{itemize}
	\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
	\item Small number of layers create micellar structure
	\item Beyond 20 layers is unnecessary to get expected configuration
\end{itemize}

The starting distance between layers was chosen so that energy minimization occured with no errors due to overlaps. 
\begin{itemize}
	\item Layers collapse to favorable layer-to-layer distance within first few picoseconds of equilibration 
\end{itemize}

\noindent The remaining parameters were chosen based on experimental data. 
\begin{itemize}
	\item SAXS to get Pore-to-Pore
	\item TEM images estimate pore size
\end{itemize}

\noindent NPT simulations were run at 300 K and 1 bar for system equilibration. 
\begin{itemize}
	\item Monitored 'hexagonality'
	\item Pores don't show perfect hexagonal character for short sims (~20 ns) 
	\item We see a smaller average pore-to-pore distance than reported
	\item Varied initial pore-to-pore distance and ran very long simulations
	\item Starting pore-to-pore distances of 4.0 and 4.5 converge to same average with long\textbf{er} sims 
\end{itemize}

After an equilibrated structure was created, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
\begin{itemize}
	\item Crosslinking maintains alignment of cylindrical mesophases
	\item head to tail addition
	\item Details of crosslinking algorithm (refer to appendix or supplemental info)
\end{itemize}

\noindent The crosslinked system was then solvated with water to mimic a membrane in water.
\begin{itemize}
	\item x ns sims run to allow full water penetration into pores
	\item simulated isotropically with enough water in between periodic images
\end{itemize}

\section{Results and Discussion}

The final, equilibrated system had pores which were spaced 3.5 nm apart. This is the thermotropic phase though. More to come once system is solvated.

Other things to be studied:
\begin{itemize}
	\item Monomers per layer
	\begin{itemize}
		\item Questions: How many monomers are in each layer? Do we observe pi stacking of benzene rings as hypothesized in papers? Are there even defined layers?
		\item Hypothesis: There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature. While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains. Staying completely ordered, stacked on top of each other is not entropically favorable.
	\end{itemize}
	\item Self diffusion of sodium in pores
	\begin{itemize}
		\item Past literature reports ions arranged in a circle about pore walls leaving void space as a pore. Simulation show that they may be arranged gaussian-like	
		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules. 
		\item Questions to be studied: Do sodium counter-ions stay bound to carbonyl groups? Do sodium ions that get through the membrane need to go all the way through or do they cause some sort of momentum transfer that pushes a different ion out of the pore on the opposite side? Is there ion diffusion through hydrophobic matrix? Is it negligible? What happens to the chlorine ion in NaCl?
		\item Hypothesis: Sodium ions that are already acting as counterions stay mostly bound to their functional groups. Sodium ions diffusing through from bulk salt water need to diffuse all the way through and drag along a chlorine atom to maintain charge neutrality. Sodium ions tethered to chloride may exchange with sodium ions bound to monomer. There is negligible diffusion of sodium chloride through hydrophobic matrix.
	\end{itemize}
	\item Diffusion of water in pores
	\begin{itemize}
		\item Questions to be studied: How easily does water diffuse through the pores (permeability)? Is there diffusion at all through the hydrophobic matrix? If so, is it negligible? Is there a hydration shell around entering salt? Do waters get stripped from hydration shell? How does water interact with sodium ions? Is water transport faster down the center of the pore? Do water molecules orient themselves in a specific way at the pore walls?
		\item Hypothesis: Water molecules will travel with through the pores with a parabolic laminar-like trajectory. Water molecules along the wall will be hindered as they get stuck in the hydrophilic head groups causing slower transport at the walls -- This hypothesis will depend on what I see once I solvate and equilibrate the system with water. I think the arrangement of sodium ions will change when solvated (That could be an intersting conclusion in itself). No water will be transported through hydrophobic regions.    
	\end{itemize}
	\item Compare rates of diffusion of water and sodium to estimate selectivity and rejection
	\begin{itemize}
		\item I am studying this because they are the two parameters to be optimized ultimately
	\end{itemize}
\end{itemize}

\section{Conclusion}

In this work, a molecular model has been developed which can predict transport in an lyotropic liquid crystal membrane. 
\begin{itemize}
	\item Results presented for HII phase monomer but can be adapted to other LLCs
	\item Model can be used for prediction of transport properties in new membranes
\end{itemize}

\end{document}

### 2016-08-17 Ben_Manuscripts/Paper1/Outline.tex
outline comments.
Update Outline.tex

@@
 
-Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which may be feasible for large scale production.
+	Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which are feasible for large scale production.
 	\begin{itemize}
@@
 
+	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
+	\begin{itemize}
+		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
+		\begin{itemize}
+			\item This could change how one thinks about molecules diffusing through membrane
+			\item Could also be a difference between lyotropic and thermotropic phases
+		\end{itemize}
+		\item How many monomers are in a layer?
+		\begin{itemize}
+			\item There is no clear answer to this question in literature. I'd like to confirm or deny past predictions
+		\end{itemize}
+		\item What is the equilibrium water content in lyotropic phase?
+		%BJC: There is a paper which synthesizes the membrane with different starting water content in solution.
+They find no difference in the final structure of the of the membrane with water contents ranging from 7 - 10 %.
+I want to see what the water content is at equilibrium as a way to inform experimentalists who are doing sythesis -- It's not super important but it addresses a question that has been asked in the past.
+	\end{itemize}
+
 	A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
@@
 		performance bottle necks and direct design of future monomers/membranes
-	\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
-	\begin{itemize}
-		\item This could change how one thinks about molecules diffusing through membrane
-		\item Could also be a difference between lyotropic and thermotropic phases
-	\end{itemize}
+		%MRS: this is getting to be a lot of points under this.
+Talking about the specifically understood mechanisms should probably be a separate thesis, perhaps outlining the specific questions that are not known about these membranes.
+		%BJC: There isn't much in the literature about specifically understood mechanisms for the HII phase.
+All of the discussion pertains to the bicontinuous cubic phase.
+The Donnan model applies to both in theory so I could talk more about that.
+There are also the generic membrane transport equations relating flux to applied pressure, pore size, membrane thickness etc.
+based on Hagen-Poiseuille flow in the pores.
 		\item Will we observe Donnan exclusion or some variation on it at the pore entrance
 		\item What are the relative weights of steric and electrical effects that deterimine selectivity -- is there an optimal balance
-	\item How many monomers are in a layer?
-	\item What is the equilibrium water content in lyotropic phase?
-	\item We can vary the following to make predictions about new systems:
 		\begin{itemize}
-		\item Liquid crystal used - or a mixture of different liquid crystals
-		\item Minor structural variations (e.g. 7, 8, , 9, 10, 11 ... CH2's in the tails)
-		\item Counterion -- Size/valence of counterion
-		\item Functional head groups
+			\item Look at Coulombic vs. Lennard Jones interactions
+			\item Do ions or water have trouble getting through because of interactions with other things in the pores (e.g. ions, water, carbonyl groups, benzene rings)
+			\item Does concentration of ions in the pore repel incoming ions?
 		\end{itemize}
-	\item How does varying these things effect pore separation, pore size, phase stability, and transport and why are these effects observed 
 	\end{itemize}
@@
 
-HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16. All molecular dynamics simulations were run using Gromacs version 5.1.2.
+	HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16.
+All molecular dynamics simulations were run using Gromacs version 5.1.2.
 
@@
 	The final, equilibrated system had pores which were spaced 3.5 nm apart. This is the thermotropic phase though. More to come once system is solvated. 
+	\newline 
+	\newline \noindent Questions to be answered and experiments to test them:
 
-Other things to be studied:
 	\begin{itemize}
-	\item Monomers per layer
+		\item Question: How many monomers are in each layer? Do we even see defined layers?
 		\begin{itemize}
-		\item Questions: How many monomers are in each layer? Do we observe pi stacking of benzene rings as hypothesized in papers? Are there even defined layers?
-		\item Hypothesis: There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature.
+			\item \textbf{Why this is important:} 
+				\item We can understand how monomer shape/size/length influence pore density
+				\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed.
+				\item We can see whether the effects of pi stacking are as pronounced as hypothesized in other papers.
+					\item fixed-charge models may underpredict pi-stacking -- searching for a reference to confirm this although that would make sense. How would this limit what we can say about the pore structure?
+			\item \textbf{Experiments to be run:}
+				\item Use membrane thickness and approximate pore size to define cylindrical disk regions. Measure number of monomers in these regions
+				\item Visualization will help too
+			\item \textbf{Hypothesis:} There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature.
 While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains.
@@
 		\end{itemize}
-	\item Self diffusion of sodium in pores
+		\item What is the mechanism of sodium transport through the pores?
 		\begin{itemize}
-		\item Past literature reports ions arranged in a circle about pore walls leaving void space as a pore. Simulation show that they may be arranged gaussian-like	
+			\item \textbf{Why this is important:}
+			\item Past literature reports ions arranged in a circle about pore walls leaving void space as a pore. Simulations show that they may be arranged gaussian-like	
 			\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
-		\item Questions to be studied: Do sodium counter-ions stay bound to carbonyl groups?
-Do sodium ions that get through the membrane need to go all the way through or do they cause some sort of momentum transfer that pushes a different ion out of the pore on the opposite side?
-Is there ion diffusion through hydrophobic matrix?
-Is it negligible?
-What happens to the chlorine ion in NaCl?
-		\item Hypothesis: Sodium ions that are already acting as counterions stay mostly bound to their functional groups.
+			\item  Experimentalists may be over-predicting flux through pores because they view it as a hollow channel.
+			%MRS: should make it clearer why each of these questions matter - how would knowing the answers improve the ability to make predictions about macroscopic membrane properties?
+			\item \textbf{Experiments to be run and what they can tell us:} 
+				\item Measure timescales of counter-ions binding to carbonyl groups. The residence time of a sodium ion -- get scripts from Drew.
+				\item Observe positions of bulk sodium ions over time.
+					\item Do they go all the way through or do they cause some sort of momentum transfer that pushes a different ion out of the pore on the opposite side?
+I would expect higher rejections if the sodium ion is required to diffuse all the way through
+				\item See if we can observe ion diffusion through hydrophobic matrix. Is it negligible? If it's not negligible, there is whole new issue to consider
+				\item Observe influence of chlorine ion in NaCl? The hydrated NaCl has to fit in the pore. Does it ion exchange with bound sodiums.
+			\item \textbf{Hypothesis:} Sodium ions that are already acting as counterions stay mostly bound to their functional groups.
 Sodium ions diffusing through from bulk salt water need to diffuse all the way through and drag along a chlorine atom to maintain charge neutrality.
@@
 		\end{itemize}
-	\item Diffusion of water in pores
+		\item What is the mechanism of water transport through the pores?
 		\begin{itemize}
-		\item Questions to be studied: How easily does water diffuse through the pores (permeability)?
-Is there diffusion at all through the hydrophobic matrix?
-If so, is it negligible?
-Is there a hydration shell around entering salt?
-Do waters get stripped from hydration shell?
-How does water interact with sodium ions?
-Is water transport faster down the center of the pore?
+			\item textbf{Why this is important:}
+			\item Bottle necks in membrane design which limit water transport will directly affect membrane performance with regard to selectivity and rejection. 
+			\item The configuration/structure of water molecules in confined regions is not well understood
+			\item \textbf{Experiments to be run and what they can tell us:}
+			\item Observe hydration shell around entering salt. Do waters get stripped from hydration shell?
+			\item Quantify how much free water goes through vs. how much gets through as a part of hydration shell. More free water would mean higher water flux and higher rejection. 
+			\item Measure water transport down the center of the pore vs.
+on the pore walls.
 Do water molecules orient themselves in a specific way at the pore walls?
-		\item Hypothesis: Water molecules will travel with through the pores with a parabolic laminar-like trajectory.
+If water primarily passes through the pore center, maybe there is a modification that can be made so the walls are 'slippery-er' and more water can get through.
+			\item \textbf{Hypothesis}: Water molecules will travel with through the pores with a parabolic laminar-like trajectory.
 Water molecules along the wall will be hindered as they get stuck in the hydrophilic head groups causing slower transport at the walls -- This hypothesis will depend on what I see once I solvate and equilibrate the system with water.
@@
 		\end{itemize}
-	\item Compare rates of diffusion of water and sodium to estimate selectivity and rejection
+		\item What are the relative rates of diffusion of water and sodium? 
 		\begin{itemize}
-		\item I am studying this because they are the two parameters to be optimized ultimately
+			\item \textbf{Why this is important:}
+			\item The relative rates of diffusion are ultimately what characterizes a membrane's performance. These are what must be optimized.
+			\item \textbf{Experiments to be run:}
+			\item Calculate diffusion of water and sodium. 
+			\item Use these values to calculate selectivity and rejection
+		\end{itemize}
+		\item How can we validate the model?
+		\begin{itemize}
+			\item textbf{Why this is important:}
+			\item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
+			\item \textbf{Experiments to Run:}
+			\item Direct comparison of conductivity measurements to experimental results
+			\item SAXS structural comparisons
 		\end{itemize} 
 	\end{itemize}
-
+	\section{Future Work}
+	We can vary the following to make predictions about new systems:
+		\begin{itemize}
+			\item Liquid crystal used - or a mixture of different liquid crystals
+			\item Minor structural variations (e.g. 7, 8, , 9, 10, 11 ... CH2's in the tails)
+			\item Counterion -- Size/valence of counterion
+			\item Functional head groups
+			\item How does varying these things effect pore separation, pore size, phase stability, and transport and why are these effects observed
+		\end{itemize} 
 	\section{Conclusion}

### 2016-09-12 Ben_Manuscripts/Paper1/Paper1_nosolvation.tex
Create Paper1_nosolvation.tex

--- 2016-08-17 Ben_Manuscripts/Paper1/Outline.tex
@@
 		\end{itemize}
-		\item What is the equilibrium water content in lyotropic phase?
-		%BJC: There is a paper which synthesizes the membrane with different starting water content in solution.
-They find no difference in the final structure of the of the membrane with water contents ranging from 7 - 10 %.
-I want to see what the water content is at equilibrium as a way to inform experimentalists who are doing sythesis -- It's not super important but it addresses a question that has been asked in the past.
 	\end{itemize}
@@
 		performance bottle necks and direct design of future monomers/membranes
-		%MRS: this is getting to be a lot of points under this.
-Talking about the specifically understood mechanisms should probably be a separate thesis, perhaps outlining the specific questions that are not known about these membranes.
-		%BJC: There isn't much in the literature about specifically understood mechanisms for the HII phase.
-All of the discussion pertains to the bicontinuous cubic phase.
-The Donnan model applies to both in theory so I could talk more about that.
-There are also the generic membrane transport equations relating flux to applied pressure, pore size, membrane thickness etc.
-based on Hagen-Poiseuille flow in the pores.
 		\item Will we observe Donnan exclusion or some variation on it at the pore entrance
@@
 			\item Look at Coulombic vs. Lennard Jones interactions
-			\item Do ions or water have trouble getting through because of interactions with other things in the pores (e.g. ions, water, carbonyl groups, benzene rings)
+			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
 			\item Does concentration of ions in the pore repel incoming ions?
@@
 		\item Observations of transport mechanism
-		\item The model is consistent with experiments and ready to extend to other systems
+		\item The model is consistent with experiments and will be used in water flux predictions
 	\end{itemize}
@@
 	\begin{itemize}
+		\item Layers close enough together to prevent layers from slipping between each other
 		\item Layers collapse to favorable layer-to-layer distance within first few picoseconds of equilibration 
@@
 	\noindent NPT simulations were run at 300 K and 1 bar for system equilibration.
+	% Include new equilibration scheme here? 
 	\begin{itemize}
@@
 
-	\noindent The crosslinked system was then solvated with water to mimic a membrane in water.
-	\begin{itemize}
-		\item x ns sims run to allow full water penetration into pores
-		\item simulated isotropically with enough water in between periodic images
-	\end{itemize}
-
 	\section{Results and Discussion}
 
-	The final, equilibrated system had pores which were spaced 3.5 nm apart. This is the thermotropic phase though. More to come once system is solvated. 
+	The final, equilibrated system had pores which were spaced 4.2 nm apart.
 	\newline 
@@
 		\end{itemize}
-		\item What is the mechanism of sodium transport through the pores?
+		\item How do sodium counterions behave inside the pores and what influence might they have on membrane performance?
 		\begin{itemize}
@@
 			\item  Experimentalists may be over-predicting flux through pores because they view it as a hollow channel.
-			%MRS: should make it clearer why each of these questions matter - how would knowing the answers improve the ability to make predictions about macroscopic membrane properties?
 			\item \textbf{Experiments to be run and what they can tell us:} 
-				\item Measure timescales of counter-ions binding to carbonyl groups. The residence time of a sodium ion -- get scripts from Drew.
-				\item Observe positions of bulk sodium ions over time.
-					\item Do they go all the way through or do they cause some sort of momentum transfer that pushes a different ion out of the pore on the opposite side?
-I would expect higher rejections if the sodium ion is required to diffuse all the way through
-				\item See if we can observe ion diffusion through hydrophobic matrix. Is it negligible? If it's not negligible, there is whole new issue to consider
-				\item Observe influence of chlorine ion in NaCl? The hydrated NaCl has to fit in the pore. Does it ion exchange with bound sodiums.
-			\item \textbf{Hypothesis:} Sodium ions that are already acting as counterions stay mostly bound to their functional groups.
-Sodium ions diffusing through from bulk salt water need to diffuse all the way through and drag along a chlorine atom to maintain charge neutrality.
-Sodium ions tethered to chloride may exchange with sodium ions bound to monomer.
-There is negligible diffusion of sodium chloride through hydrophobic matrix.
-		\end{itemize}
-		\item What is the mechanism of water transport through the pores?
-		\begin{itemize}
-			\item textbf{Why this is important:}
-			\item Bottle necks in membrane design which limit water transport will directly affect membrane performance with regard to selectivity and rejection. 
-			\item The configuration/structure of water molecules in confined regions is not well understood
-			\item \textbf{Experiments to be run and what they can tell us:}
-			\item Observe hydration shell around entering salt. Do waters get stripped from hydration shell?
-			\item Quantify how much free water goes through vs. how much gets through as a part of hydration shell. More free water would mean higher water flux and higher rejection. 
-			\item Measure water transport down the center of the pore vs.
-on the pore walls.
-Do water molecules orient themselves in a specific way at the pore walls?
-If water primarily passes through the pore center, maybe there is a modification that can be made so the walls are 'slippery-er' and more water can get through.
-			\item \textbf{Hypothesis}: Water molecules will travel with through the pores with a parabolic laminar-like trajectory.
-Water molecules along the wall will be hindered as they get stuck in the hydrophilic head groups causing slower transport at the walls -- This hypothesis will depend on what I see once I solvate and equilibrate the system with water.
-I think the arrangement of sodium ions will change when solvated (That could be an intersting conclusion in itself).
-No water will be transported through hydrophobic regions.
-		\end{itemize}
-		\item What are the relative rates of diffusion of water and sodium? 
-		\begin{itemize}
-			\item \textbf{Why this is important:}
-			\item The relative rates of diffusion are ultimately what characterizes a membrane's performance. These are what must be optimized.
-			\item \textbf{Experiments to be run:}
-			\item Calculate diffusion of water and sodium. 
-			\item Use these values to calculate selectivity and rejection
+				\item Measure Ionic Conductivity as a direct comparison to experiment -- speculate about the mechanism of ionic conduction and how it can be improved by changing the microscopic structure
+				\item Measure Ionic Conduction on early equilibration membrane which shows defined pores
+			\item \textbf{Hypothesis:} Sodium ions are arranged across each pore radius according to a gaussian distribution.
+This organization leads to higher ionic conductivity because ions are more mobile, while an ordered pore restricts the ability of ions to hop to different sites.
 		\end{itemize}
@@
 	\end{itemize}
-	\section{Future Work}
 	We can vary the following to make predictions about new systems:
@@
 
-	In this work, a molecular model has been developed which can predict transport in an lyotropic liquid crystal membrane. 
+	In this work, a molecular model has been developed which can predict transport in an thermotropic liquid crystal membrane. 
 	\begin{itemize}
-		\item Results presented for HII phase monomer but can be adapted to other LLCs
+		\item Results presented for HII phase monomer but can be adapted to other LCs
 		\item Model can be used for prediction of transport properties in new membranes

### 2016-10-12 Ben_Manuscripts/Paper1/Prelim_report.tex
Add files via upload

\documentclass[12pt]{article}
\usepackage{fixltx2e}
\title{Understanding transport in the H\textsubscript{II} Phase of Lyotropic Liquid Crystal Membranes}
\author{Benjamin J. Coscia\\
	Advisors: Michael Shirts, Richard Noble, Douglas Gin}
\usepackage[margin=1in]{geometry}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{cleveref}
\captionsetup{font=small}
\begin{document}
\bibliographystyle{ieeetran}
\maketitle
\section{Objective Statement}

Experimentalists lack a reliable procedure for identifying the best material for producing inverse hexagonal phase (H\textsubscript{II}) Lyotropic Liquid Crystal (LLC) membranes. Small angle X-ray scattering (SAXS) measurements confirm the hexagonal crystalline structure exhibited by the self-assembling liquid crystal (LC) monomers \cite{smith_ordered_1997}. TEM images support the hypothesis that the pores are aligned, straight, uniform in size and on the order of 1 nm in diameter \cite{feng_scalable_2014, feng_thin_2016}. Experiments tell us that the membrane selectively passes water while rejecting solutes on the order of 1 nm in diameter \cite{zhou_supported_2005}. Aside from heuristic arguments and fitting experimental data to constrained macroscopic models, we lack an understanding of why these membranes behave the way they do and consequently have no way of systematically improving them. All characterization and improvement has been done using a single starting monomer with, at most, minor variations to its structure. There are certainly other materials or derivatives which exhibit similar behavior with improved properties which is why there is a need for a reliable atomistic model that can explore a much wider chemical space. It is my goal to develop an accurate molecular model which accurately describes the microscopic structure and properties of H\textsubscript{II} LLC membranes. I will first develop a model based on the current membrane and experimental data and study it using Molecular Dynamics (MD) simulations. The procedure used in its development will then be generalized as a method for fast development of models of other potential H\textsubscript{II} forming LLC monomers. The flexibility of MD, efficient algorithms and mass computing power, will allow fast, relative to experiment, screening of large numbers of candidates. Viable candidates will be suggested to experimentalists for validation with an eventual feedback loop between experiment and modeling which will lead to optimized H\textsubscript{II} LLC membranes designed for a specific application.

\section{Significance}
H\textsubscript{II} LLC membranes were originally designed to see whether useful materials could be controllably synthesized at the nanometer scale \cite{smith_ordered_1997}. Their use has since been targeted as nanofiltration (NF) membranes for size selective filtration of molecules 1-10 nm in diameter \cite{zhou_supported_2005}. It is hypothesized that they can be used for desalination \cite{feng_scalable_2014} and general water treatment, such as cleaning up fracking water. Separation of solutes on the order of 1 nanometer in diameter during water treatment and desalination is a multi-faceted challenge requiring a process that is selective, high throughput and low energy \cite{daily_population_1992}. Membrane based processes have already been widely implemented in order to control water quality and composition. NF and reverse osmosis (RO) membranes are well suited for this purpose \cite{lee_review_2011, greenlee_reverse_2009, humplik_nanostructured_2011}. NF membrane have pore sizes on the order of 1 nm in size which separates solutes on the basis of size exclusion and, in the case of polarizable or charged solutes, electrostatic repulsions  \cite{humplik_nanostructured_2011}. RO separates based on the relative solubilities and diffusivities of solutes in the membrane’s dense polymer matrix \cite{wijmans_solution-diffusion_1995}. Despite the difference in the mechanism of solute transport in each type of membrane, the flux of solute through the membrane can be shown to be proportional to the applied pressure and inversely proportional to the membrane thickness \cite{wijmans_solution-diffusion_1995}. Hence, maximum throughput can be achieved by increasing the applied pressure and by making very thin membranes. Unfortunately, controlling membrane architecture is near impossible using conventional polymer membrane synthetic techniques. NF membranes typically have tortuous pores, increasing the effective membrane thickness, with a distribution of pore radii, limiting selectivity \cite{lau_recent_2012}. Since RO membranes rely on the diffusive motion of solutes through the polymer matrix, the path followed by solutes is tortuous. The membrane’s density also requires much higher applied pressures driving up energy costs. Materials used for RO are limited as well since they must be chosen based on its interaction with desired separation solute \cite{fritzmann_state---art_2007}.

H\textsubscript{II} LLC membranes have straight, uniform, nanometer scale pores which can give optimal throughput given a sufficiently thin membrane. Additionally, the chemistry of the LC monomer used to assemble the membrane can be changed \cite{zhou_supported_2005} presumably leading to different solute rejecting properties. They can be tailored to specific applications including not only nanofiltration and desalination, but gas separations and as selective vapor barriers \cite{gin_polymerized_2008}, and even as templates for catalytic particles and functional groups \cite{ding_catalytic_2000}. The culmination of this remains to be seen through modeling and experimentation, but the impact of this technology working as hypothesized can lead to a revolution in membrane technology.

\section{Background and Literature Review}
Nanostructured membrane materials are particularly promising because they offer nanoscale control \cite{humplik_nanostructured_2011}. Solute rejecting pores can be tuned to appropriate sizes for size exclusion filtration, functional groups can be added to enhance selectivity, and pore shape and size are well-defined which all facilitate better performance and performance prediction.

Nanostructured materials are not without limitations. Leading nanostructured filtration technologies include graphene sheets, carbon nanotubes (CNTs), and metal organic frameworks (MOFs). Graphene sheets are atomically thick which gives excellent permeability, but in practice, defects are easily introduced during manufacturing which severely decreases performance \cite{cohen-tanugi_multilayer_2016}. Molecular dynamic studies of carbon nanotube embedded membranes have shown their ability to completely reject solutes. Developing synthetic methods to achieve the same pore uniformity and alignment that was simulated is a significant challenge for implementation beyond the lab scale \cite{mauter_environmental_2008}. MOFs are a successful nanostructured technology particularly for gas separation applications because of their ability to selectively adsorb gases such as CH\textsubscript{4} and H\textsubscript{2}. Unfortunately, they are unstable in water making them ineffective nanofiltration membranes \cite{dias_towards-2015}.

Lyotropic Liquid Crystals (LLCs) offer the opportunity to create highly ordered membrane structures with tunable properties for a variety of applications including desalination and wastewater treatment. This class of organic compounds forms a range of crystalline phases including lamellar, bicontinuous cubic and hexagonal phases based on monomer structure and initial solution composition \cite{lee_polymerization_1995, smith_ordered_1997}.

The structure of the LLC materials has the potential to address demands in wastewater treatment and desalination. In the presence of c.a. 10 \% water, the monomer to be studied in this paper, shown in figure 1, forms the H\textsubscript{II} phase consisting of vertically aligned nanopores of uniform size, packed in a hexagonal array \cite{smith_ordered_1997,resel_structural_2000}. In the absence of water a thermotropic columnar phase, termed Col\textsubscript{h}, self assembles into the same hexagonal morphology, absent of water, and is stable up to its isotropic transition point at 65.6 \degree C. Hydrophilic regions of monomer are oriented inward forming aqueous pores. Until recently, this type of behavior was only seen in mesoscopic domains with no macroscopic pore alignment which prevented competitive fluxes\cite{zhou_supported_2005}. Feng et al. has since been able to manipulate the material into membrane sheets with uniform alignment using electromagnetic alignment and soft confinement techniques, followed by a free radical crosslinking reaction used to maintain the film’s structure\cite{feng_scalable_2014,feng_thin_2016}. With this advance, further experimental work is being done to characterize LLC membranes. Nearly straight pores combined with Donnan exclusion and molecular sieving promise a future LLC H\textsubscript{II} phase membrane offering high permeability and selectivity with subsequent low energy consumption.
\begin{figure}
\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\linewidth]{monomer.png}
		\label{fig:monomer}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering % material in its scope will be centered
		\includegraphics[width=\linewidth]{Top_View_4_3.png}
		\label{fig:TopView}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Side_Profile.png}
		\label{fig:SideProfile}
		\caption{}
	\end{subfigure}
	\caption{(a) Monomer Na-GA3C11 (b) Top View of hexagonally packed system made with Na-GA3C11. Sodium ions are colored blue. Red lines are vinyl groups from each tail of the monomer (c) Side Profile of hexagonally packed system. Sodium ions are emphasized in blue to show that the pores run straight through the membrane}
	\label{fig:System}
\end{figure}
Modeling LLC systems, in particular the H\textsubscript{II}  and Col\textsubscript{h} phases, is new to the field, however we can draw on work done on similar systems from other fields in order to inform our own work. Biological ion channels have long been studied using MD simulations. Ion channels are embedded into cell membranes and gate ion passage into cells inducing a membrane potential and regulating cell volume. Methods used to measure ion conduction in ion channels are being adapted to the LLC system for direct comparison to experiment. \cite{aksimentiev_imaging_2005, gumbart_constant_2012}. CNTs have been extensively studied with MD and exhibit fast water conduction through the membrane pores. Techniques used to study the mechanism of water and solute transport in CNTs are necessary to understand transport mechanisms in LLCs \cite{zhu_water_2003}.

\section{Methods}

H\textsubscript{II} monomers were parameterized using the Generalized Amber Forcefield (GAFF) with the Antechamber package provided with AmberTools16\cite{case_ambertools16_2016,wang_development_2004, wang_automatic_2006}. All molecular dynamics simulations are run using Gromacs 5.1.2 and later versions as they are released \cite{bekker_gromacs:_1993, berendsen_gromacs:_1995, lindahl_gromacs_2001, van_der_spoel_gromacs:_2005, hess_gromacs_2008}. Long, computationally intensive simulations are run using the HPC resources Janus and Bridges \cite{nystrom_bridges:_2015, towns_xsede:_2014}.

An assembly code was written in python to place parameterized and energy minimized monomers into the expected cylindrical form (Figure \ref{fig:TopInit}). A monoclinic unit cell was chosen since it is the smallest unit cell which will still form a hexagonal packing. Four pores consisting of stacked rings of monomer were placed inside the unit cell with hydrophilic head groups oriented towards the center of the pore. Number of layers, number of monomers per layer, pore radius, distance between pore centers, and distance between layers are all adjustable parameters along with the monomer chosen to build the structure.

\begin{wrapfigure}{R}{0.3\textwidth}
	\centering
	\includegraphics[width=0.3\textwidth]{Top_Init.png}
	\caption{\label{fig:TopInit} A top down view of the initial configuration created using the assembly python script}
\end{wrapfigure}

Although in the limit of infinite time, the system will settle into its lowest energy configuration, the H\textsubscript{II} phase, the length of time for the system to reach that state varies with choice of starting conditions. To equilibrate fastest, and avoid entrapment in metastable states, choice of initial configuration dimensions are best chosen according to developed guidelines (available upon request).

Following creation of an initial structure, simulations are run at 300 K and 1 bar (The NPT ensemble). From a visual perspective, the pores stay packed in a hexagonal configuration (See Figure \ref{fig:System}b). To address subtleties which the eye cannot see, a set of tools were coded to monitor system equilibration. One of the most useful tools quantifies the ‘hexagonality’ of the system. To do so, the x and y coordinates of the sodium of ions in each pore were averaged and treated as a central axis running straight down in each pore. The distance between these axes were used to quantify the hexagonal character of the system. In a perfectly hexagonal system, all pore-to-pore distances would be equal. To achieve this character, simulations greater than 100 ns were necessary.

After equilibration, the system is solvated with water then simulated further to allow water molecules to naturally penetrate the hydrophilic pores. Alternatively, one can skip the water solvation step to study the thermotropic Col\textsubscript{h} system. Whichever route is chosen, it is necessary to follow equilibration with a crosslinking reaction. Macroscopically this is an important step in order to maintain long range pore alignment. Microscopically it is important as a way to make sure we are modeling the exact system. It also locks in the equilibrium structure and eliminates any worries about fluctuations away from it.

A generic crosslinking algorithm is not available and thus required the creation of my own based on my knowledge of the crosslink reaction and work done by other authors on similar systems \cite{jang_relative_2012}. The crosslinking reaction is a free radical polymerization of terminal vinyl groups on each of the three monomer tails. On a high level, the algorithm calculates distances between potentially bonding carbons after a short simulation. Carbons meeting a distance cutoff criteria are bonded together or terminated with a specified probability. Carbons that would be left as radicals are flagged as a way to increase reactivity on future iterations. The process is repeated until reasonable bonds between eligible carbons can no longer be made.

The careful development of this methodology will make it applicable to other LLC systems.

\section{Progress to Date}

(‘lots’ of pictures in this section)
The first phase of this project has been defined by the development of an accurate membrane model. To date, that goal is nearly achieved. The system has yet to be fully solvated but there is experimental data of the thermotropic Colh phase which parallels that of the H\textsubscript{II} phase and can be used in the development of the model. Using this experimental data as a benchmark, we have created an LLC system that equilibrates to a geometry consistent with TEM and SAXS data. (Figure). The spacing between pores is 4.14 +/- 0.05 nm. The radius of the pores, as defined by the ring of highest sodium density, are 1.2 nm. Also, a reliable crosslinking procedure has been implemented which can lock in the equilibrium structure of the membrane and match the real system.
The last step in model validation requires that the model accurately predicts experimental conductivity measurements. In the process, I will develop a general method for measuring conductivity based on MD output. To date, I have identified three possible routes for making these predictions. The Nernst Einstein relation is the simplest and is based on ion diffusivity… Fluctation-dissipation theorem … CompEL type technique. 
In parallel, I have learned how to best utilize the HPC resources available by conducting scaling studies on each resources. I have learned how and developed methods to optimally parallelize Gromacs simulations on Janus and Bridges using both MPI and GPUs. This will allow us to run more simulations in a shorter amount which will be instrumental to high throughput screening.

\section{Research Plan}

My immediate goals, which I hope to complete by my first thesis committee meeting are to have developed a fully validated molecular model of H\textsubscript{II} LLC systems. Beyond just matching experimental data, I would like learn more about the structure that experiments cannot tell us. A major question of interest to me is understanding how many monomer are in each disk that make up the membrane pores. As it stands, it is unclear whether there are 5, 6, 7 or some combination of these amounts stacked in alternating layers. I will assemble reasonable structures and conduct free energy calculations to make clear which ensemble the membrane system is most stable in. This is a computationally expensive task that may prove necessary if we see inconsistent property predictions between models made up of different compositions. Additionally, I plan to understand the mechanism of solute transport for a few select molecules. I am particularly interested in the transport of sodium chloride as I’d like to see this membrane applied as a desalination technology.
My long term goals are to use the model to direct membrane design in the Gin and Noble labs. I plan to create an organized and versatile python package which can be used to design LLC membranes for separation of small molecules of choice. If possible, I’d like to develop my own macroscopic model which can be used to predict structures without the computational expensive of MD simulations. I plan to get in the lab myself and get to work designing these advanced materials. Ultimately I hope to make the design of LLC membranes more systematic and fast.

\bibliography{Prelim}

\end{document}

### 2016-11-17 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Outline for 1st paper updated

--- 2016-09-12 Ben_Manuscripts/Paper1/Paper1_nosolvation.tex
@@
 			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
-			\item Zeolites - Good rejections/selectivities, but low flux and high cost of manufacturing. Generally limited to applications needing thermal/chemical resistance
 		\end{itemize}
@@
 		\item Until recently, they could not be aligned - hindered progress
-		\item Talk about Yale alignment techniques
+		\item Yale aligns them
 		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
@@
 		\item Beyond 20 layers is unnecessary to get expected configuration
-	\end{itemize}
-
-	The starting distance between layers was chosen so that energy minimization occured with no errors due to overlaps. 
-	\begin{itemize}
-		\item Layers close enough together to prevent layers from slipping between each other
-		\item Layers collapse to favorable layer-to-layer distance within first few picoseconds of equilibration 
+		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
 	\end{itemize}
@@
 		\item SAXS to get Pore-to-Pore
-		\item TEM images estimate pore size
+		\item TEM images and rejection give a pore size estimate
 	\end{itemize}
@@
 	\noindent NPT simulations were run at 300 K and 1 bar for system equilibration.
-	% Include new equilibration scheme here? 
 	\begin{itemize}
@@
 
-	The final, equilibrated system had pores which were spaced 4.2 nm apart.
-	\newline 
-	\newline \noindent Questions to be answered and experiments to test them:
-
+	The validity of our model can be tested based on its agreement with experimental structural and material property data
 	\begin{itemize}
-		\item Question: How many monomers are in each layer? Do we even see defined layers?
-		\begin{itemize}
-			\item \textbf{Why this is important:} 
-				\item We can understand how monomer shape/size/length influence pore density
-				\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed.
-				\item We can see whether the effects of pi stacking are as pronounced as hypothesized in other papers.
-					\item fixed-charge models may underpredict pi-stacking -- searching for a reference to confirm this although that would make sense. How would this limit what we can say about the pore structure?
-			\item \textbf{Experiments to be run:}
-				\item Use membrane thickness and approximate pore size to define cylindrical disk regions. Measure number of monomers in these regions
-				\item Visualization will help too
-			\item \textbf{Hypothesis:} There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature.
-While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains.
-Staying completely ordered, stacked on top of each other is not entropically favorable.
-		\end{itemize}
-		\item How do sodium counterions behave inside the pores and what influence might they have on membrane performance?
-		\begin{itemize}
-			\item \textbf{Why this is important:}
-			\item Past literature reports ions arranged in a circle about pore walls leaving void space as a pore. Simulations show that they may be arranged gaussian-like	
-			\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
-			\item  Experimentalists may be over-predicting flux through pores because they view it as a hollow channel.
-			\item \textbf{Experiments to be run and what they can tell us:} 
-				\item Measure Ionic Conductivity as a direct comparison to experiment -- speculate about the mechanism of ionic conduction and how it can be improved by changing the microscopic structure
-				\item Measure Ionic Conduction on early equilibration membrane which shows defined pores
-			\item \textbf{Hypothesis:} Sodium ions are arranged across each pore radius according to a gaussian distribution.
-This organization leads to higher ionic conductivity because ions are more mobile, while an ordered pore restricts the ability of ions to hop to different sites.
-		\end{itemize}
-		\item How can we validate the model?
-		\begin{itemize}
-			\item textbf{Why this is important:}
 		\item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
-			\item \textbf{Experiments to Run:}
+		\item Tougher with a large system for which no force fields have been specifically developed
 		\item Direct comparison of conductivity measurements to experimental results
@@
 	\end{itemize}
+
+	A structurally accurate and reproducible model of the Colh phase LLC membrane has been developed
+	\begin{itemize}
+		\item Visual perspective - show top view and cross section
+		\item System validated using multiple monomer configurations (working on this now)
+		\item Pore to pore distance
+		\begin{itemize}
+			\item We know from SAXS data what the distance between pores should be
+			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
+			\item Effect of crosslinking
+		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
+		\item Density - there are crude lab measurements which my model is in agreement with (no one has reported any values since it wasn't relevant to them)
 		\end{itemize}
-	We can vary the following to make predictions about new systems:
+	\end{itemize}
+
+	The monomers are arranged into disks containing __ monomers in each layer. (Or are there defined layers -- I need to test this idea a bit more) 
+	\begin{itemize}
+		\item Hypothesis: There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature.
+While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains.
+Staying completely ordered, stacked on top of each other is not entropically favorable.
+		\item We can understand how monomer shape/size/length influence pore density
+		\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed.
+
+	Sodium counterions are distributed randomly within the hydrophilic pore regions. (I should actually come up with a distribution e.g. gaussian)
+	\begin{itemize}
+		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore. Simulations show that they are not 	
+		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
+		\item  Experimentalists may be over-predicting flux through pores because they view it as a hollow channel.
+
+	The model gives reasonable estimates of ionic conductivity.
+	\begin{itemize}
+		\item There are a few ways to estimate ionic conductivity as seen in literature. We prefer a method which can extract an estimate based purely on an equilibrium trajectory
+		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
+		\item We must also account for the azimuthal distributions, linking our perfectly straight microscopic system to the not-so-straight macroscopic system
+		\item Two methods used to for prediction
+		\item Nernst Einstein Relation:
+		\begin{itemize}
+			\item Widely used equation for estimating ionic conductivity
+			\item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
+			\item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
+			\item Concentration is concentration of ions in the whole membrane, not just channels
+		\end{itemize}
+		\item Collective Diffusion:
+		\begin{itemize}
+			\item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
+			\item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
+			\item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
+			\item A similar model has been derived and validate to predict water permeability using equilibrium simulations
+			\item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores.
+One would expect single channel IC to be much larger than the bulk membrane
+			\item This model suggests that changing the structure of the monomer tails may actually improve conductivity (I don't know how feasible this would actually be, they'd need to be charged somehow) 
+			\item Changing the valence of the counterion may also increase ionic conductivity (I need to actually test this by increasing the charge on sodium for a calculation)
+	\end{itemize}
+
+	Our model can be used to evaluate other liquid crystalline assemblies
 		\begin{itemize}
 			\item Liquid crystal used - or a mixture of different liquid crystals
-			\item Minor structural variations (e.g. 7, 8, , 9, 10, 11 ... CH2's in the tails)
+			\item Minor structural variations (e.g. 7, 8, 9, 10, 11 ... CH2's in the tails)
 			\item Counterion -- Size/valence of counterion
@@
 		\end{itemize}
+
 	\section{Conclusion}
@@
 	\begin{itemize}
-		\item Results presented for HII phase monomer but can be adapted to other LCs
+		\item Results presented for Colh phase monomer but can be adapted to other LCs
 		\item Model can be used for prediction of transport properties in new membranes
+		\item Yet to solvate system to establish procedures for HII phase prediction
 	\end{itemize}

### 2016-11-22 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updated outline.

@@
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-\author{Benjamin J. Coscia, Michael R. Shirts, Douglas L. Gin, Richard D. Noble}
+%\author{Benjamin J. Coscia, Michael R. Shirts, Douglas L. Gin, Richard D. Noble}
+\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} % usually the PI would be the last author.
 \begin{document}
@@
 	\section{Introduction}
-
+%MRS: make sure the introduction asks all the questions that will be answered by the results presented, and doesn't raise questions that are never brought up again. 	
+%MRS: possibly we want to look at the more detailed X-ray diffraction patterns, but that may not be feasible on the timescale.
 	Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
@@
 	\end{itemize} 
-
+%MRS: don't need to use capitals, even if it will become an acronym.
+%MRS: also it's self-assembled LLC's that are an alternative, not
+%LLC's in general.  
 	Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which are feasible for large scale production.
@@
 	\end{itemize}
-
+%MRS: might want to include effective pore radius.	
 	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
@@
 		\item Will we observe Donnan exclusion or some variation on it at the pore entrance
+%MRS: Are we going to restrict this paper to dry membranes?
+That might be the best way to have a reasonable length paper out in a reasonable amount of time.
+Follow up with water paper.
+Donnan exclusion.
 		\item What are the relative weights of steric and electrical effects that deterimine selectivity -- is there an optimal balance
 		\begin{itemize}
+%MRS: breaking into Coulombic vs.
+Lennard-Jones doesnt' really help that much.
+We can brainstorm other ways to examine it.
+The cleanest is to run separate simulations with electrostatics turned off, because it's the free energy that matters, not different components of the potential energy
 			\item Look at Coulombic vs. Lennard Jones interactions
@@
 			\item Does concentration of ions in the pore repel incoming ions?
+%MRS: we might want to restrict to what happens INSIDE the ring rather than entering/exiting, since the entrance/exit will differ a lot between pores with and without water.
 		\end{itemize}
 	\end{itemize}
-
+%MRS: launch a new phase might be overkill. Enable a qualitatively different type of membrane design.	
 	A physically accurate molecular model with easily modified structural features will launch a new phase of research into directing design of an optimal LLC membrane.
@@
 
+%MRS: there isn't a single most suitable monomer structure, so should rephrase it.
+Also, suitable is not defined.
+So perhaps ``an ensemble of characteristic low-energy vacuum monomoer configurations were constructed''
 	The most suitable monomer structural configuration was decided by applying a simulated annealing process to the parameterized monomer. 
@@
 	\begin{itemize}
-		\item Work done that shows coarse grain model self assembly in ~1000 ns
-		\item Attempts with HII system not fruitful
+		\item Work done that shows coarse grain model self assembly in ~1000 ns %MRS: include citation in outline if important for the logic.
+		\item Attempts with HII system not fruitful  %MRS: will eventually report what didn't work.
 		\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
@@
 		\item This is the thermotropic phase, information used depends on thermotropic experimental data
+%MRS: somewhere in the outline there should be a description of the difference between thermotropic and lyotropic phases.
 	\end{itemize}
@@
 	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
+%MRS: worth it to describe the extent to which the final structure is independent of parameters. 
 	\begin{itemize}
@@
 		\item Pores don't show perfect hexagonal character for short sims (~20 ns) 
+                  %MRS: but does the short time behavior really matter?
 		\item We see a smaller average pore-to-pore distance than reported
@@
 		\item SAXS structural comparisons
+%MRS: this seems a bit repetitive - SAXS structural comparisons and conductivity are brought up in a few places.  Want to make it a cleaner outline. 
 	\end{itemize}
@@
 
-	The monomers are arranged into disks containing __ monomers in each layer. (Or are there defined layers -- I need to test this idea a bit more) 
+	The monomers are arranged into disks containing XXXX monomers in each layer. (Or are there defined layers -- I need to test this idea a bit more) 
 	\begin{itemize}
@@
 Staying completely ordered, stacked on top of each other is not entropically favorable.
+%MRS: one thing we could to to test to see if pi-pi stacking could order them.
+We introduce an explicit dipole in the middle of the aromatic ring, all aligned (I can show you how to set this up using the virtual_sites command).
+We see how strong it neds to be in order to make the rings line up - or if any strength will really create that ordering.
+One could imagine that when the dipole gets strong enough, it just pulls ions out of the channel.
 		\item We can understand how monomer shape/size/length influence pore density
+%MRS: I'm not quite sure how the next sentence fits in. You mean we want to design a membrane that has more pores, and so we want materials with larger pores?
 		\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed.
@@
 		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore. Simulations show that they are not
+%MRS: I think we need to be a litte.
+If we see that the pores form this way under a variety of conditions (just the ones we've looked at - different numbers of monomers per layer, different spacing, then that provides strong evidence that the more aligned form is less probable.
 		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
@@
 			\item This model suggests that changing the structure of the monomer tails may actually improve conductivity (I don't know how feasible this would actually be, they'd need to be charged somehow) 
+%MRS: interesting idea, but probably we don't want to explore it that much here.
+It also seems counterintuitive, since the charge in the tails is essentially trapped -- there is fluctuation, but it is trapped rather than free.
 			\item Changing the valence of the counterion may also increase ionic conductivity (I need to actually test this by increasing the charge on sodium for a calculation)
+%MRS: increasing charge on the sodium alone probably won't work that well unless you also increase the charge on the carboxylate, since you will then have a lack of electroneutrality.
 	\end{itemize}
@@
 		\item Results presented for Colh phase monomer but can be adapted to other LCs
+%MRS: will need to describe more what the differences are.  Is it just whether it's solvated or not? (i.e. different compositions, but structures are similar?)
 		\item Model can be used for prediction of transport properties in new membranes
 		\item Yet to solvate system to establish procedures for HII phase prediction
+%MRS: rather than saying yet to do it, describe it for future work.                  
 	\end{itemize}

### 2016-11-22 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updating outline

@@
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-%\author{Benjamin J. Coscia, Michael R. Shirts, Douglas L. Gin, Richard D. Noble}
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} % usually the PI would be the last author.
@@
 	\end{itemize} 
-%MRS: don't need to use capitals, even if it will become an acronym.
-%MRS: also it's self-assembled LLC's that are an alternative, not
-%LLC's in general.  
-	Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which are feasible for large scale production.
+	Self assembling lyotropic liquid crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques feasible for large scale production.
 	\begin{itemize}
 		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
-		\item My monomer forms HII phase consisting of vertically aligned, monodisperse, straight pores in a hexagonal array
+		\item My monomer forms the Colh phase consisting of aligned 
 		\item Hydrophilic regions point towards pore centers
@@
 %MRS: might want to include effective pore radius.
+%BJC: I'm not sure how to include the pore radius since we don't have a clear method for its measurement (experimentally and consequently
+%via simulations). I don't know that we can answer that question which is why I didn't pose it in the intro	
 	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
@@
 	\begin{itemize}
-		\item HII phase studies currently limited mostly to one monomer with minor variations
+		\item Colh phase studies currently limited mostly to one monomer with minor variations
 		\item Current optimization efforts performed through trial and error
@@
 		performance bottle necks and direct design of future monomers/membranes
-		\item Will we observe Donnan exclusion or some variation on it at the pore entrance
 %MRS: Are we going to restrict this paper to dry membranes?
@@
 Donnan exclusion.
-		\item What are the relative weights of steric and electrical effects that deterimine selectivity -- is there an optimal balance
+%BJC: I think restricting the paper to dry membranes (Colh phase) is a good idea, especially since I don't have much to say about the HII phase yet. 
 		\begin{itemize}
@@
 The cleanest is to run separate simulations with electrostatics turned off, because it's the free energy that matters, not different components of the potential energy
-			\item Look at Coulombic vs. Lennard Jones interactions
+%BJC: Ok, I removed mention of that - We won't study electrostatic/coulombic interactions until we are looking in depth at transport mechanism anyways - right?
 			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
@@
 %MRS: we might want to restrict to what happens INSIDE the ring rather than entering/exiting, since the entrance/exit will differ a lot between pores with and without water.
+%BJC: Ok, removed the point about end effects
 		\end{itemize}
@@
 %MRS: launch a new phase might be overkill. Enable a qualitatively different type of membrane design.	
-	A physically accurate molecular model with easily modified structural features will launch a new phase of research into directing design of an optimal LLC membrane.
+	A physically accurate molecular model with easily modified structural features will enable a qualitatively different type of membrane design aimed optimization of self assembled LLC membranes.
 	\begin{itemize}

### 2016-11-22 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updating outline

@@
 		\end{itemize}
+		%BJC - I'm going to cut this since I cannot answer this question definitively - unless we take an approach based on enthalpy differences and structural comparisons (pore-to-pore distance and x-ray scattering data).
+We probably have enough information for a speculative answer, but I don't know if that should be included in the paper
 		\item How many monomers are in a layer?
@@
 	\end{itemize}
-%MRS: launch a new phase might be overkill. Enable a qualitatively different type of membrane design.	
 	A physically accurate molecular model with easily modified structural features will enable a qualitatively different type of membrane design aimed optimization of self assembled LLC membranes.
@@
 		\item Observations of transport mechanism
-		\item The model is consistent with experiments and will be used in water flux predictions
+		\item The model is consistent with experiments and will be used in solvent/solute flux and solute rejection predictions
 	\end{itemize}

### 2016-11-22 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updating Outline

@@
 		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
-		\item My monomer forms the Colh phase consisting of aligned 
+		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII) - explain difference 
 		\item Hydrophilic regions point towards pore centers
@@
 		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
+		\item This paper will focus on the development of a model of the colh phase
 	\end{itemize}
@@
 	\begin{itemize}
+		\item Two types of self assembled LLCs have been made - thermotropic and lyotropic -- explain difference -- shift focus to Colh
 		\item Colh phase studies currently limited mostly to one monomer with minor variations
@@
 
-%MRS: there isn't a single most suitable monomer structure, so should rephrase it.
-Also, suitable is not defined.
-So perhaps ``an ensemble of characteristic low-energy vacuum monomoer configurations were constructed''
-	The most suitable monomer structural configuration was decided by applying a simulated annealing process to the parameterized monomer. 
+	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
 	\begin{itemize}
@@
 		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
+		\item New configurations reparamaterized
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Work done that shows coarse grain model self assembly in ~1000 ns %MRS: include citation in outline if important for the logic.
-		\item Attempts with HII system not fruitful  %MRS: will eventually report what didn't work.
+		\item Work done that shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
+		\item Attempts with Colh system not fruitful  %MRS: will eventually report what didn't work. %BJC Will we not report it here?
 		\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
@@
 %MRS: somewhere in the outline there should be a description of the difference between thermotropic and lyotropic phases.
+%BJC: added in the intro around line 28 
 	\end{itemize}
@@
 %MRS: worth it to describe the extent to which the final structure is independent of parameters.  
+%BJC: So, mention how starting pore-to-pore affects the equilibrium structure, how different crosslinking parameters affect crosslinked structure etc.? Or are you just talking about crosslinking?
 	\begin{itemize}
@@
 	\begin{itemize}
-		\item Monitored 'hexagonality'
-		\item Pores don't show perfect hexagonal character for short sims (~20 ns) 
-                  %MRS: but does the short time behavior really matter?
-		\item We see a smaller average pore-to-pore distance than reported
+		\item Monitored 'hexagonality' - i.e. how the distance between pores compares to an ideal hexagon
 		\item Varied initial pore-to-pore distance and ran very long simulations
-		\item Starting pore-to-pore distances of 4.0 and 4.5 converge to same average with long\textbf{er} sims 
+		\item Starting pore-to-pore distances of 4.0 and 4.5 converge to same average with longer sims 
 	\end{itemize}
@@
 		\item head to tail addition
+		\item racemic mixture 
 		\item Details of crosslinking algorithm (refer to appendix or supplemental info)
@@
 %MRS: this seems a bit repetitive - SAXS structural comparisons and conductivity are brought up in a few places.  Want to make it a cleaner outline. 
+%BJC: Okay, I can probably delete this paragraph from this section. Maybe the structural stuff is better worked into the methods section since it is really about model development. 
+%BJC: The ionic conductivity measurement and reason for them will be made clear once I actually start talking about it 
 	\end{itemize}
@@
 One could imagine that when the dipole gets strong enough, it just pulls ions out of the channel.
+%BJC: I remember us talking about this during one of our meetings. I assume this shouldn't be too hard to set up and simulate before the paper is submitted?
 		\item We can understand how monomer shape/size/length influence pore density
 %MRS: I'm not quite sure how the next sentence fits in. You mean we want to design a membrane that has more pores, and so we want materials with larger pores?
+%BJC: What I'm trying to say is that if we can make the membrane more porous - closer together pores mostly - then we can presumably increase ionic conductivity and permeability
 		\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed.
@@
 		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore. Simulations show that they are not
-%MRS: I think we need to be a litte.
+%MRS: I think we need to be a litte careful.
 If we see that the pores form this way under a variety of conditions (just the ones we've looked at - different numbers of monomers per layer, different spacing, then that provides strong evidence that the more aligned form is less probable.
+%BJC: So by be careful, you mean word it a little more delicately, for example: "Simulations under a variety of conditions suggest that ions prefer disorder within the pores"
 		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
@@
 One would expect single channel IC to be much larger than the bulk membrane
-			\item This model suggests that changing the structure of the monomer tails may actually improve conductivity (I don't know how feasible this would actually be, they'd need to be charged somehow) 
-%MRS: interesting idea, but probably we don't want to explore it that much here.
-It also seems counterintuitive, since the charge in the tails is essentially trapped -- there is fluctuation, but it is trapped rather than free.
 			\item Changing the valence of the counterion may also increase ionic conductivity (I need to actually test this by increasing the charge on sodium for a calculation)
 %MRS: increasing charge on the sodium alone probably won't work that well unless you also increase the charge on the carboxylate, since you will then have a lack of electroneutrality.
+%BJC: right, that makes sense.
+In which case, the fluctuations might cancel and give similar conductivity - maybe I'll just stay away from it for now.
+I just though it might be nices to have some hypotheses
+%about how to improve ionic conductivity based just on the modeling done so far.
 	\end{itemize}
@@
 
-	In this work, a molecular model has been developed which can predict transport in an thermotropic liquid crystal membrane. 
+	In this work, a molecular model has been developed intended to predict transport in a thermotropic liquid crystal membrane. 
 	\begin{itemize}
@@
 %MRS: will need to describe more what the differences are.  Is it just whether it's solvated or not? (i.e. different compositions, but structures are similar?)
+%BJC: I'm not sure I follow, differences between what exactly? All I am trying to say is that we can stick other monomers in place of NAGA3C11 and see what happens.
 		\item Model can be used for prediction of transport properties in new membranes
-		\item Yet to solvate system to establish procedures for HII phase prediction
-%MRS: rather than saying yet to do it, describe it for future work.                  
+		\item We will solvate the system to establish procedures for HII phase prediction
 	\end{itemize}

### 2016-11-28 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updated Outline
Updated outline.

@@
 		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
-		\item This paper will focus on the development of a model of the colh phase
+		\item This paper will focus on the development of a model of the colh phase since it is a simpler starting point and has just as much experimental data
 	\end{itemize}
@@
 %via simulations). I don't know that we can answer that question which is why I didn't pose it in the intro	
+%MRS2: if no measurement experimentally, don't need one for simulation at this point!
 	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
@@
 		\end{itemize}
-		%BJC - I'm going to cut this since I cannot answer this question definitively - unless we take an approach based on enthalpy differences and structural comparisons (pore-to-pore distance and x-ray scattering data).
+		%BJC - I'm likely going to cut this since I cannot answer this question definitively - unless we take an approach based on enthalpy differences and structural comparisons (pore-to-pore distance and x-ray scattering data).
 We probably have enough information for a speculative answer, but I don't know if that should be included in the paper
+                %MRS: I think it's probably useful to report which arrangements are stable and give consistent pore-to-pore distances.
+Also can help answer the questions whether there are distinct well-separated ``layers'', or if it's more complicated.
 		\item How many monomers are in a layer?
@@
 		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
+                 %MRS: say what you mean by reparameterized.
+Charges recalculated?
+Are the charges different from configuration to configuration (hopefully not).
+Were multiple configurations used in the reparameterization?
 		\item New configurations reparamaterized
@@
 		\item Work done that shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
-		\item Attempts with Colh system not fruitful  %MRS: will eventually report what didn't work. %BJC Will we not report it here?
+		\item Attempts with Colh system not fruitful  
+                  %MRS: will eventually report what didn't work . 
+                  %BJC Will we not report it here?
+                  %MRS2: no, I meant you eventually will put here what didn't work.
 		\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
@@
 %BJC: added in the intro around line 28 
+%MRS2: the two are blended together a bit making it hard to see what is investigated where. We can discuss this today.
 	\end{itemize}
@@
 %BJC: So, mention how starting pore-to-pore affects the equilibrium structure, how different crosslinking parameters affect crosslinked structure etc.? Or are you just talking about crosslinking?
+%MRS2: I'm just talking about building the system (before crosslinking) - distance between starting config, length of time equilibrated.
+Because this is how you are showing that the builds procedure is reasonable and leads to similar structures independently of how you build it.
+Crosslinking later.
 	\begin{itemize}
@@
 	The monomers are arranged into disks containing XXXX monomers in each layer. (Or are there defined layers -- I need to test this idea a bit more) 
+	%BJC: Do you think this point is even worth attacking at the moment?
+        %MRS2: we sort of need to do this to convince ourselves that this approach is reasonable, so we should include it and show others it is reasonable.
 	\begin{itemize}
@@
 %BJC: I remember us talking about this during one of our meetings. I assume this shouldn't be too hard to set up and simulate before the paper is submitted?
+%MRS2: we can talk about what would need to be done.  We need to get the dipole in the right direction for each monomer. 
 		\item We can understand how monomer shape/size/length influence pore density
@@
 %BJC: What I'm trying to say is that if we can make the membrane more porous - closer together pores mostly - then we can presumably increase ionic conductivity and permeability
+%MRS2: OK, you want to put this where it is connected directly with the other information.
+Perhaps the thesis of it's own paragraph, with supporting sentences about how one could use MD simulations to do this?
 		\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed. 
-
+	\end{itemize}
 	Sodium counterions are distributed randomly within the hydrophilic pore regions. (I should actually come up with a distribution e.g. gaussian)
@@
 %BJC: So by be careful, you mean word it a little more delicately, for example: "Simulations under a variety of conditions suggest that ions prefer disorder within the pores"
+%MRS2: yes.
+%MRS2: below -- hinder transport of what?
+Both other ions and water?
+Probably need to explain more clearly what people though before about whether they hindered transport or not in order to show that the role is ``different than previously thought''
 		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
+%MRS2: should be careful, since they are not necessarily predicting flux yet.  We do know that they have good ionic conductivity. 
 		\item  Experimentalists may be over-predicting flux through pores because they view it as a hollow channel.
-
+        \end{itemize}	
 	The model gives reasonable estimates of ionic conductivity.
@@
 		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
+%MRS2: clarify in what situations the azimuthal distribution is necessary.
 		\item We must also account for the azimuthal distributions, linking our perfectly straight microscopic system to the not-so-straight macroscopic system
@@
 			\item Changing the valence of the counterion may also increase ionic conductivity (I need to actually test this by increasing the charge on sodium for a calculation)
+                \end{itemize}                    
 %MRS: increasing charge on the sodium alone probably won't work that well unless you also increase the charge on the carboxylate, since you will then have a lack of electroneutrality.
@@
 %BJC: I'm not sure I follow, differences between what exactly? All I am trying to say is that we can stick other monomers in place of NAGA3C11 and see what happens.
+%MRS2: got it.
 		\item Model can be used for prediction of transport properties in new membranes

### 2016-11-29 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Edited outline

@@
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} % usually the PI would be the last author.
+\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
 \begin{document}
@@
 		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
-		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII) - explain difference 
+		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII) - explain difference % actually explain 
 		\item Hydrophilic regions point towards pore centers
@@
 Also can help answer the questions whether there are distinct well-separated ``layers'', or if it's more complicated.
+		%BJC : try five
 		\item How many monomers are in a layer?
@@
 Were multiple configurations used in the reparameterization?
+		%BJC: Openeye software to get the best charge for multiple configurations.
 		\item New configurations reparamaterized
@@
 %MRS2: clarify in what situations the azimuthal distribution is necessary.
+%BJC: don't explicity say azimuthal
 		\item We must also account for the azimuthal distributions, linking our perfectly straight microscopic system to the not-so-straight macroscopic system

### 2016-11-29 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updated Outline

--- 2016-11-22 Ben_Manuscripts/Paper1/Paper1_Outline.tex
@@
 	\section{Introduction}
-%MRS: make sure the introduction asks all the questions that will be answered by the results presented, and doesn't raise questions that are never brought up again. 	
-%MRS: possibly we want to look at the more detailed X-ray diffraction patterns, but that may not be feasible on the timescale.
 	Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
@@
 		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
-		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII) - explain difference 
+		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII) 
+		\item The thermotropic, Colh is formed by the self assembly of neat monomer
+		\item The lyotropic, HII phase is formed in the presence of small percentages of water (around 8 percent)
+		\item Both assemble into cyclinders with hydrophilic groups oriented inward towards the pore center and hydrophobic group facing outward.
+The only difference is the inclusion of water in the structure which leads to minor variations in the structure with potentially different filtration properties (although no filtration experiments have been done on Colh)
 		\item Hydrophilic regions point towards pore centers
 		\item Until recently, they could not be aligned - hindered progress
-		\item Yale aligns them
+		\item Yale aligns them, then crosslinks them to lock in the structure
 		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
-		\item This paper will focus on the development of a model of the colh phase
+		\item This paper will focus on the development of a model of the colh phase since it is a simpler starting point and has just as much experimental data
 	\end{itemize}
-%MRS: might want to include effective pore radius.
-%BJC: I'm not sure how to include the pore radius since we don't have a clear method for its measurement (experimentally and consequently
-%via simulations). I don't know that we can answer that question which is why I didn't pose it in the intro	
 	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
@@
 		\end{itemize}
-		%BJC - I'm going to cut this since I cannot answer this question definitively - unless we take an approach based on enthalpy differences and structural comparisons (pore-to-pore distance and x-ray scattering data).
-We probably have enough information for a speculative answer, but I don't know if that should be included in the paper
 		\item How many monomers are in a layer?
@@
 			\item There is no clear answer to this question in literature. I'd like to confirm or deny past predictions
+			% BJC: It seems that the following discussion should be placed in the results section, with the above lines belonging in this section, posing the question along with past work/justification
+			\item It has been suggested that there are 4 monomers in a each disk/layer, however, simulations have shown that this leads to unstable configurations with dimensions that are too small compared to experiment.
+			\item Stable simulations with 6 and 7 monomers have been performed (will do one with five soon) which give structural characteristics consistent with experiment
+			\item Stable systems have also been simulated consisting of varying numbers of monomers per layer
+			\item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
 		\end{itemize}
@@
 		performance bottle necks and direct design of future monomers/membranes
-%MRS: Are we going to restrict this paper to dry membranes?
-That might be the best way to have a reasonable length paper out in a reasonable amount of time.
-Follow up with water paper.
-Donnan exclusion.
-%BJC: I think restricting the paper to dry membranes (Colh phase) is a good idea, especially since I don't have much to say about the HII phase yet. 
 		\begin{itemize}
-%MRS: breaking into Coulombic vs.
-Lennard-Jones doesnt' really help that much.
-We can brainstorm other ways to examine it.
-The cleanest is to run separate simulations with electrostatics turned off, because it's the free energy that matters, not different components of the potential energy
-%BJC: Ok, I removed mention of that - We won't study electrostatic/coulombic interactions until we are looking in depth at transport mechanism anyways - right?
 			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
 			\item Does concentration of ions in the pore repel incoming ions?
-%MRS: we might want to restrict to what happens INSIDE the ring rather than entering/exiting, since the entrance/exit will differ a lot between pores with and without water.
-%BJC: Ok, removed the point about end effects
 		\end{itemize}
@@
 		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
-		\item New configurations reparamaterized
+		%BJC: Openeye software to get the best charge for multiple configurations.
+		\item New configurations used for reparamaterization, BUT most likely will just use one set of charges for one configuration since I've done 90 percent of simulations based on one parameterization.
+In the future, I will have a single set of parameters.
 	\end{itemize}
@@
 		\item Work done that shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
-		\item Attempts with Colh system not fruitful  %MRS: will eventually report what didn't work. %BJC Will we not report it here?
+		\item Attempts with Colh system not fruitful  
+		\begin{itemize}
+			\item Packed monomers into box
+			\item Simulated for ~100 ns with no real progress shown towards self assembly
+		\end{itemize}  
 		\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
@@
 		\item This is the thermotropic phase, information used depends on thermotropic experimental data
-%MRS: somewhere in the outline there should be a description of the difference between thermotropic and lyotropic phases.
-%BJC: added in the intro around line 28 
+	\end{itemize}
+
+        The validity of our model can be tested based on its agreement with experimental structural and material property data
+        \begin{itemize}
+                \item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
+                \item Tougher with a large system for which no force fields have been specifically developed
 	\end{itemize}
@@
 	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
-%MRS: worth it to describe the extent to which the final structure is independent of parameters.  
-%BJC: So, mention how starting pore-to-pore affects the equilibrium structure, how different crosslinking parameters affect crosslinked structure etc.? Or are you just talking about crosslinking?
 	\begin{itemize}
@@
 	\begin{itemize}
-		\item SAXS to get Pore-to-Pore
+		\item SAXS to get an idea of Pore-to-Pore
+		\begin{itemize}
+			\item multiple starting pore to pore distances tested (3.0, 3.5, 4.0, 4.5 nm)
+			\item 4.0 nm and 4.5 nm converged to similar dimensions, 4.5 nm was most reliable
+		\end{itemize}
 		\item TEM images and rejection give a pore size estimate
@@
 		\item Monitored 'hexagonality' - i.e. how the distance between pores compares to an ideal hexagon
-		\item Varied initial pore-to-pore distance and ran very long simulations
-		\item Starting pore-to-pore distances of 4.0 and 4.5 converge to same average with longer sims 
+		\item Varied initial pore-to-pore distance and ran very long simulations - typically > 200 ns
 	\end{itemize}
@@
 	\section{Results and Discussion}
-
-	The validity of our model can be tested based on its agreement with experimental structural and material property data
-	\begin{itemize}
-		\item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
-		\item Tougher with a large system for which no force fields have been specifically developed
-		\item Direct comparison of conductivity measurements to experimental results
-		\item SAXS structural comparisons
-%MRS: this seems a bit repetitive - SAXS structural comparisons and conductivity are brought up in a few places.  Want to make it a cleaner outline. 
-%BJC: Okay, I can probably delete this paragraph from this section. Maybe the structural stuff is better worked into the methods section since it is really about model development. 
-%BJC: The ionic conductivity measurement and reason for them will be made clear once I actually start talking about it 
-	\end{itemize}
 
@@
 Staying completely ordered, stacked on top of each other is not entropically favorable.
-%MRS: one thing we could to to test to see if pi-pi stacking could order them.
-We introduce an explicit dipole in the middle of the aromatic ring, all aligned (I can show you how to set this up using the virtual_sites command).
-We see how strong it neds to be in order to make the rings line up - or if any strength will really create that ordering.
-One could imagine that when the dipole gets strong enough, it just pulls ions out of the channel.
-%BJC: I remember us talking about this during one of our meetings. I assume this shouldn't be too hard to set up and simulate before the paper is submitted?
-		\item We can understand how monomer shape/size/length influence pore density
-%MRS: I'm not quite sure how the next sentence fits in. You mean we want to design a membrane that has more pores, and so we want materials with larger pores?
-%BJC: What I'm trying to say is that if we can make the membrane more porous - closer together pores mostly - then we can presumably increase ionic conductivity and permeability
-		\item Ideally we'd want as many pores as possible per membrane area. More monomers per layer means more material needed and less pores formed.
+	        \item It has been suggested that there are 4 monomers in a each disk/layer, however, simulations have shown that this leads to unstable configurations with dimensions that are too small compared to experiment.
+                \item Stable simulations with 6 and 7 monomers have been performed (will do one with five soon) which give structural characteristics consistent with experiment
+                \item Stable systems have also been simulated consisting of varying numbers of monomers per layer
+                \item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
+	\end{itemize}
 
@@
 	\begin{itemize}
-		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore. Simulations show that they are not
-%MRS: I think we need to be a litte careful.
-If we see that the pores form this way under a variety of conditions (just the ones we've looked at - different numbers of monomers per layer, different spacing, then that provides strong evidence that the more aligned form is less probable.
-%BJC: So by be careful, you mean word it a little more delicately, for example: "Simulations under a variety of conditions suggest that ions prefer disorder within the pores"
-		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules.
-		\item  Experimentalists may be over-predicting flux through pores because they view it as a hollow channel.
+		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore.
+Simulations under a variety of conditions suggest that ions prefer disorder within the pores.
+		\item A size exclusion mechanism has been proposed in the past, however that might no be the only force at play
+		\item Ions may play a role in transport, hindering flux of solute and solvent by slowing their diffusion
+		\item Experimentalists may be over-estimating the potential for high solvent flux through the pores because they view it as a hollow channel.
+The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes.
+%BJC: This seems dark and unencouraging but I think it's true.
+Maybe I shouldn't talk about it for now.
+        \end{itemize}
 
@@
 		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
-		\item We must also account for the azimuthal distributions, linking our perfectly straight microscopic system to the not-so-straight macroscopic system
+		\item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system
 		\item Two methods used to for prediction
@@
 One would expect single channel IC to be much larger than the bulk membrane
-			\item Changing the valence of the counterion may also increase ionic conductivity (I need to actually test this by increasing the charge on sodium for a calculation)
-%MRS: increasing charge on the sodium alone probably won't work that well unless you also increase the charge on the carboxylate, since you will then have a lack of electroneutrality.
-%BJC: right, that makes sense.
-In which case, the fluctuations might cancel and give similar conductivity - maybe I'll just stay away from it for now.
-I just though it might be nices to have some hypotheses
-%about how to improve ionic conductivity based just on the modeling done so far.
+                \end{itemize}                    
 	\end{itemize}
@@
 		\item Results presented for Colh phase monomer but can be adapted to other LCs
-%MRS: will need to describe more what the differences are.  Is it just whether it's solvated or not? (i.e. different compositions, but structures are similar?)
-%BJC: I'm not sure I follow, differences between what exactly? All I am trying to say is that we can stick other monomers in place of NAGA3C11 and see what happens.
 		\item Model can be used for prediction of transport properties in new membranes

### 2016-12-09 Ben_Manuscripts/Paper1/Manuscript.tex
Starting writing up methods/ system setup section

--- 2016-11-29 Ben_Manuscripts/Paper1/Paper1_Outline.tex
@@
 
-	HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16.
+	Col\subscript{h} phase forming monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16.
 All molecular dynamics simulations were run using Gromacs version 5.1.2.
-
 An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
-	\begin{itemize}
-		\item Initially parameterized monomer gives unfavorable structure
-		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
-		\item Result not global minimum but close enough for structure building
-		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
-		%BJC: Openeye software to get the best charge for multiple configurations.
-		\item New configurations used for reparamaterization, BUT most likely will just use one set of charges for one configuration since I've done 90 percent of simulations based on one parameterization.
-In the future, I will have a single set of parameters.
-	\end{itemize}
+The structure was cooled from 1000 to 50 K over the course of 10 nanoseconds, resulting in a structure suitable for packing into a simulation box.
+Multiple configurations were saved from the annealing trajectory to be used in parallel in order to prove independence of starting configuration.
+A new set of parameters was generated from the annealed structure and used for all configurations tested.
 
 	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable simulation length.
-	\begin{itemize}
-		\item Work done that shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
-		\item Attempts with Colh system not fruitful  
-		\begin{itemize}
-			\item Packed monomers into box
-			\item Simulated for ~100 ns with no real progress shown towards self assembly
-		\end{itemize}  
-		\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
-		\item Code has adjustable parameters: Pore-to-Pore distance, pore radius, number of monomer layers (justification for parameters chosen in following paragraphs)
-		\item This is the thermotropic phase, information used depends on thermotropic experimental data
-	\end{itemize}
+Past work has shown the ability of other liquid crystals to form into various phases including the hexagonal phase using coarse grain models in c.a.
+1000 ns.
+While 1000 ns would be expensive with an atomistic model, it is not an unreasonable amount of time and prompted an attempt at a self assembly.
+480 monomers were packed into a cubic box using Packmol software, with box dimensions chosen based on approximate density of the col\subscript{h} phase.
+The box was made slightly larger than this to help with Packmol convergence and to give the monomers room to reorient themselves during equilibration.
+NPT simulations were carried out for 100 ns.
+In that time, no visible progress was made towards self assembly so simulations were stopped.
+Even if self assembly happened eventually, it is not a sustainable way to set up the system due to computational cost.
 
-        The validity of our model can be tested based on its agreement with experimental structural and material property data
-        \begin{itemize}
-                \item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
-                \item Tougher with a large system for which no force fields have been specifically developed
-	\end{itemize}
+	A script was written to place monomers into a configuration close to the expected equilibrium structure in order to minimize equilibration time.
+The code makes copies of monomers and rotates them to form disks with a hydrophilic center.
+The disks are stacked on top of each other to form pores and the pores are duplicated to form a unit cell.
+The code has adjustable build parameters which should be chosen based on experimental data when possible.
+Parameters include number of monomers in a disk, the number of disks stacked on top of each in each pore, the distance between the stacked disks, the distance between pores, and the pore radius as defined by the distance between a chosen atom in the monomer and the axis around which the monomers are rotated to form the disks.
+In all simulations, an initial configuration consisting of four pores was packed into a monoclinic unit cell.
+The monoclinic unit cell with an angle between the x and y vectors of 60 degrees, is the smallest unit cell which will give hexagonal symmetry with periodic boundaries turned on.
+
+        The validity of our model can be tested based on its agreement with experimental structural and material property data.
+Our simulations should mimic the real system as best as possible within the limits imposed by choice of force field.
+This system is particularly difficult since there has not been a forcefield developed for it and the system has not been studied in the past.
+Therefor, parameters were chosen carefully based on the ability to reproducibly create acceptably accurate structures.
 
 	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency.
-	\begin{itemize}
-		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
-		\item Small number of layers create micellar structure
-		\item Beyond 20 layers is unnecessary to get expected configuration
-		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
-	\end{itemize}
+Using too few layers resulted in system which moved towards a micelle-like configuration.
+The number of layers was progressively increased until straight pores in a hexagonal configuration proved stable.
+Anything beyond 20 layers provided no extra information only contributing computational expense.
 
-	\noindent The remaining parameters were chosen based on experimental data. 
+	The spacing between layers has a significant impact on the system dimensions.
+It should be between 4 A and 7 A, with a recommended value of 5 A.
+A spacing below 4 angstroms risks large repulsions between layers during the first steps of simulation giving unpredictable results.
+A spacing greater than 7 A has consistently given structural dimensions that are too small.
+It is hypothesized that it is due to monomer layers slipping between each during the first picoseconds of simulation.
+The system gets locked into a metastable state from which there is no recovery.
+A spacing of 5 A allows a more gentle relaxation and subsequent relaxation into a experimentally consistent configuration.
+
+	Experimental small angle X-ray scattering results were used to inform our choice of an initial pore to pore distance.
+The peak corresponding to the d100 plane was used to estimate a distance between pores of 4.12 nm.
+The sensitivity of the system to the starting pore-to-pore distance was tested by simulating initial configurations with starting pore-to-pore distances of 3.0, 3.5, 4.0 and 4.5 nm.
+Using 3.0 and 3.5 nm resulted in a structure whose dimensions were too small.
+The significant overlap between pores at these initial conditions likely locked the pores together with no hope of separation without energy input.
+Starting pore-to-pore distances of 4.0 and 4.5 nm both converged to expected distances.
 	\begin{itemize}
@@
 	\begin{itemize}
+		\item semi-isotropic
 		\item Monitored 'hexagonality' - i.e. how the distance between pores compares to an ideal hexagon

### 2016-12-19 Ben_Manuscripts/Paper1/Manuscript.tex
Finished text for methods section. Started text for introduction

@@
 	Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
-	\begin{itemize}
-		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
-		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
-		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
-	\end{itemize}
+Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores.
+Polydispersity in pore radius limits the ability to completely reject solutes of a given size.
+Pore tortuosity decreases membrane permeability requiring high feed pressures in order to reach a reasonable throughput.
+Nanostructured materials can circumvent both issues.
+Theoretically one can precisely design solute rejecting pores that are uniform in size and run straight through the membrane resulting in optimal rejection and permeability.
 
 	Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
-	\begin{itemize}
-		\item Leading technologies and their limitations:
-		\begin{itemize}
-			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
-			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
-		\end{itemize}
-	\end{itemize} 
+Two notable examples are graphene sheets and carbon nanotubes.
+Graphene sheets are atomically thick and pores can be made uniform in size, however defects during manufacturing severly impact solute rejection.
+Currently, some researchers are investigating multilayered graphene sheets which should be more mechanically robust and still provide high performance.
+Carbon nanotubes have shown great promise from molecular dynamics simulations exhibiting surprisingly high water permeability, but current synthetic techniques are unable to achieve the necessary alignment and pore monodispersity which would set them apart from other technologies.
+
 	Self assembling lyotropic liquid crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques feasible for large scale production.
@@
 480 monomers were packed into a cubic box using Packmol software, with box dimensions chosen based on approximate density of the col\subscript{h} phase.
-The box was made slightly larger than this to help with Packmol convergence and to give the monomers room to reorient themselves during equilibration.
+The box was made about 10 percent larger than this to help with Packmol convergence and to give the monomers room to reorient themselves during equilibration.
 NPT simulations were carried out for 100 ns.
 In that time, no visible progress was made towards self assembly so simulations were stopped.
-Even if self assembly happened eventually, it is not a sustainable way to set up the system due to computational cost.
+Even if self assembly happened eventually, it is not a computationally sustainable way to set up the system.
 
@@
 This system is particularly difficult since there has not been a forcefield developed for it and the system has not been studied in the past.
-Therefor, parameters were chosen carefully based on the ability to reproducibly create acceptably accurate structures.
+Therefore, parameters were chosen carefully based on the ability to reproducibly create acceptably accurate structures.
 
@@
 A spacing greater than 7 A has consistently given structural dimensions that are too small.
-It is hypothesized that it is due to monomer layers slipping between each during the first picoseconds of simulation.
+It is hypothesized that it is due to monomer layers slipping between each other during the first picoseconds of simulation.
 The system gets locked into a metastable state from which there is no recovery.
-A spacing of 5 A allows a more gentle relaxation and subsequent relaxation into a experimentally consistent configuration.
+A spacing of 5 A allows a more gentle equilibration and subsequent relaxation into a experimentally consistent configuration.
 
 	Experimental small angle X-ray scattering results were used to inform our choice of an initial pore to pore distance.
-The peak corresponding to the d100 plane was used to estimate a distance between pores of 4.12 nm.
+The peak corresponding to the d\textsubscript{100} plane was used to estimate a distance between pores of 4.12 nm.
 The sensitivity of the system to the starting pore-to-pore distance was tested by simulating initial configurations with starting pore-to-pore distances of 3.0, 3.5, 4.0 and 4.5 nm.
@@
 Starting pore-to-pore distances of 4.0 and 4.5 nm both converged to expected distances.
-	\begin{itemize}
-		\item SAXS to get an idea of Pore-to-Pore
-		\begin{itemize}
-			\item multiple starting pore to pore distances tested (3.0, 3.5, 4.0, 4.5 nm)
-			\item 4.0 nm and 4.5 nm converged to similar dimensions, 4.5 nm was most reliable
-		\end{itemize}
-		\item TEM images and rejection give a pore size estimate
-	\end{itemize}
 
-	\noindent NPT simulations were run at 300 K and 1 bar for system equilibration.
-	\begin{itemize}
-		\item semi-isotropic
-		\item Monitored 'hexagonality' - i.e. how the distance between pores compares to an ideal hexagon
-		\item Varied initial pore-to-pore distance and ran very long simulations - typically > 200 ns
-	\end{itemize}
+	Experimental pore radius measurements do not currently give a clear connection to simulations.
+Rejection studies on the H\subscript{II} phase showed the ability of the pores to completely reject solutes 1.2 nm in diameter.
+TEM images confirmed the result by approximating a pore radius based on the fluorescence of stained benzene rings in the LLC monomer.
+For that reason, the initial pore radius was initialized at 0.6 nm.
+A clear definition of the pore boundaries is yet to be defined experimentally and measurements based on simulations are based on the author's methodology until a consistent method is agreed upon.
+
+	NPT simulations run at 300 K and 1 bar with semistropic box vectors and periodic boundaries on in three dimensions.
+Equilibration was monitored quantatively by observing the distance between pores over time.
+Once the distances stopped changing (disregarding equilibrium fluctuations) the system was determined to be equilibrated.
+Typical equilibrations take about 200 ns but are run for up to 500 ns or longer to ensure our results.
 
 	After an equilibrated structure was created, a crosslinking procedure was performed in order to better parallel synthetic procedures.
-	\begin{itemize}
-		\item Crosslinking maintains alignment of cylindrical mesophases
-		\item head to tail addition
-		\item racemic mixture 
-		\item Details of crosslinking algorithm (refer to appendix or supplemental info)
-	\end{itemize}
+The primary function of crosslinking in the col\textsubscript{h} phase is to maintain its ordered structure and mechanical stability.
+A simple crosslinking algorithm was implemented to created a structure which mimics the real system.
+All crosslinking occurrs at the vinyl groups present at the end of each monomer tail.
+Only head-to-tail addition was considered since it is the mode of addition which dominates.
+Because the reaction is free radical polymerization, atoms are necessarily added to the system.
+This was achieved using dummy atoms meant to represent initiator and added hydrogens.
+The initiator was simulated as hydrogen for simplicity and should have no effect on our results because of its dilute presence.
+The overall procedure was repeated iteratively until the desired crosslinking density of 95 \% was achieved.
+During each iteration, eligible bonding carbons were determined based on their distance from other potentially bonding carbons.
+A specified percent of the distribution of eligible carbons are bonded and the topology is updated accordingly.
+Since the resultant crosslinked mixture is racemic and we are not interested in the kinetics, the orientation of bonding carbons was not considered.
+Following each iteration, a short simulation of 50 ps is run to reposition all atoms.
+Please refer to the supplemental information for detail about the algorithm.
 

### 2017-01-03 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updated outline.

@@
 		\item This paper will focus on the development of a model of the colh phase since it is a simpler starting point and has just as much experimental data
+                  %MRS: Doesn't the data appear to be that they are mostly the same in structure? Should address this to the extent we can.
 	\end{itemize}
+%MRS: don't start with the models.
+Instead something like, we wish to obtain a clearler picture of the microscopic struture, by building a model.
+Focus should always be on the physical things we are trying to study.
 	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
@@
 		\item How many monomers are in a layer?
+                %MRS: try to rewrite this the way you will in the paper -- set up the question in the introduction, and then decribe what is going on.  Raise the question, but don't answer it here.
+
 		\begin{itemize}
@@
 	\end{itemize}
+        %MRS: this is not the best way to phrase the thesis.
+I would say that we want to ask what the most likely features of the membrane are using molecular modeling.
+we can talk about the phrasing.
+But the model should not be the scientific output of the paper.
+Also, ``physically accurate'' is a high bar - it's probably not more than physically realistic.
 	A physically accurate molecular model with easily modified structural features will enable a qualitatively different type of membrane design aimed optimization of self assembled LLC membranes.
@@
 		\item Observations of transport mechanism
+                  %MRS: probably not going to make it to transport of water; validation of ion conductivity 
 		\item The model is consistent with experiments and will be used in solvent/solute flux and solute rejection predictions
+                 %MRS: these are results.
+And the focus should not also be on what you will do in the future - the focus will be on what can be read here.
+The introduction should focus on raising the questions that will be answered by the results.
 	\end{itemize}
 
+%MRS: call it methods here.
 	\section{System Setup}
@@
 	\begin{itemize}
+          %MRS: this first about unfavorable structure not relevant - people will understand it needs to equilibrated/annealed.
 		\item Initially parameterized monomer gives unfavorable structure
@@
 		%BJC: Openeye software to get the best charge for multiple configurations.
+                %MRS: should all be with the same set of charges, so its the same model.     
 		\item New configurations used for reparamaterization, BUT most likely will just use one set of charges for one configuration since I've done 90 percent of simulations based on one parameterization.
@@
 	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable simulation length. 
+%MRS: outside resonable for atomistic simulations.
 	\begin{itemize}
@@
 		\end{itemize}  
+                %MRS: features of the code not that interesting (unless making it available for others.
 		\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
@@
         \begin{itemize}
+                %MRS: this next two sentences below sort of goes w/o saying, I don't know that it needs to be emphasizd.
                 \item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
@@
 
+        %MRS: important - don't present your work chronologically, but present it to convince people of your theses.
 	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
@@
 
+        %MRS: be careful to be explicit what you mean by parameters here; people might assume FF parameters.
+        %MRS: A lot of these investigations probably belong in results, because they are answering the questions you have: what are the likely physical properties of these membranes?
+The parameters are actually variables you are investgating.
 	\noindent The remaining parameters were chosen based on experimental data. 
@@
 
+        %MRS: Results of the crosslinking are likely in results -- the fact that it didn't really change the structure of the membrame. 
 	After an equilibrated structure was created, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
@@
 
+	%MRS: not the right thesis -- focus on the physical constraints put on the membrane by the model.
 	A structurally accurate and reproducible model of the Colh phase LLC membrane has been developed
@@
 The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes.
-%BJC: This seems dark and unencouraging but I think it's true.
-Maybe I shouldn't talk about it for now.
+%BJC: This seems dark and unencouraging but I think it's true. Maybe I shouldn't talk about it for now.
+%MRS: I think the second point can be made without necessarily mentioning the first one for now.
         \end{itemize}
@@
 
+%MRS: not really a result, but can be included in the discussion. Don't need to talk too much about future work though - a paper should be focused on the current work.
 	Our model can be used to evaluate other liquid crystalline assemblies
@@
 
+        %MRS: restate in terms of the physical things learned.  THe output is knowledge, not a model.
 	In this work, a molecular model has been developed intended to predict transport in a thermotropic liquid crystal membrane. 

### 2017-01-04 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updated Outline in response to feedback -- 1-3-17

--- 2016-11-29 Ben_Manuscripts/Paper1/Paper1_Outline.tex
@@
 		\item The lyotropic, HII phase is formed in the presence of small percentages of water (around 8 percent)
-		\item Both assemble into cyclinders with hydrophilic groups oriented inward towards the pore center and hydrophobic group facing outward.
+		\item Both assemble into cylinders with hydrophilic groups oriented inward towards the pore center and hydrophobic group facing outward.
 The only difference is the inclusion of water in the structure which leads to minor variations in the structure with potentially different filtration properties (although no filtration experiments have been done on Colh)
@@
 		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
-		\item This paper will focus on the development of a model of the colh phase since it is a simpler starting point and has just as much experimental data
-	\end{itemize}
-	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
-	\begin{itemize}
-		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
-		\begin{itemize}
-			\item This could change how one thinks about molecules diffusing through membrane
-			\item Could also be a difference between lyotropic and thermotropic phases
-		\end{itemize}
-		\item How many monomers are in a layer?
-		\begin{itemize}
-			\item There is no clear answer to this question in literature. I'd like to confirm or deny past predictions
-			% BJC: It seems that the following discussion should be placed in the results section, with the above lines belonging in this section, posing the question along with past work/justification
-			\item It has been suggested that there are 4 monomers in a each disk/layer, however, simulations have shown that this leads to unstable configurations with dimensions that are too small compared to experiment.
-			\item Stable simulations with 6 and 7 monomers have been performed (will do one with five soon) which give structural characteristics consistent with experiment
-			\item Stable systems have also been simulated consisting of varying numbers of monomers per layer
-			\item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
-		\end{itemize}
+		\item The Colh phase shares the same structural features with the HII phase with the exception of the presence of water.
+This paper will focus on the development of a model of the Colh phase since it is a simpler starting point and has just as much experimental data.
+The analysis used in this paper can be readily extended to the HII phase.
+                  %MRS: Doesn't the data appear to be that they are mostly the same in structure? Should address this to the extent we can.
+		  %BJC: They're structures are almost identical (same d100 plane spacing, monomer orientation) with the exception of water being present in the HII phase.
+I rephrased the last item to make that clearer.
 	\end{itemize}
 
+	% BJC - I think that this paragraph will not be included since we are not getting into mechansims at all
         A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
@@
         \end{itemize}
-	A physically accurate molecular model with easily modified structural features will enable a qualitatively different type of membrane design aimed optimization of self assembled LLC membranes.
+
+	A clearer picture of the microscopic structure of LLC membranes, gained by building a molecular model, will change how we think about their design. 
 	\begin{itemize}
-		\item The paper will illustrate the development of a predictive molecular model
-		\item Measurements made to validate model
-		\item Observations of transport mechanism
-		\item The model is consistent with experiments and will be used in solvent/solute flux and solute rejection predictions
+		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
+		\begin{itemize}
+			\item This could change how one thinks about molecules diffusing through membrane
+			\item Could also be a difference between lyotropic and thermotropic phases
+		\end{itemize}
+		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
+		\item There is no clear answer in literature defining what that set number of monomers is. I'd like to confirm or deny past predictions
+		\begin{itemize}
+			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
+			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer
+			\item We can directly compare the plausibility of each situation along with other numbers of monomers per layer - 5, 6, 8
+			\item We can also test other, less simplistic arrangements - such as having alternating monomers per layer  %BJC: maybe leave mention of this out right and here and just address it in the results?
+		\end{itemize}
 	\end{itemize}
 
-	\section{System Setup}
+        %MRS: this is not the best way to phrase the thesis.
+I would say that we want to ask what the most likely features of the membrane are using molecular modeling.
+we can talk about the phrasing.
+But the model should not be the scientific output of the paper.
+	%BJC: Okay, tried again below, - basically what I want to communicate is that we want our model to tell us useful things and we can't do that unless we know that the model is realistic.
+We can have a good idea that it's realistic if we put thought into how we build it and if we can reproduce experimental results.
+I also want to close off the conclusion since it should be a good segway into the Methods section.
+	To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.
+	% Old thesis: A physically realistic molecular model with easily modified structural features will enable a qualitatively different type of membrane design aimed optimization of self assembled LLC membranes.
+	\begin{itemize}
+		\item This paper will illustrate the careful development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
+		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
+		\item We are primarily interested in reproducing the conclusions about structure which can be made from SAXS experiments, predicting ionic conductivity with a reasonable comparison to experiment, and reproducing experimental density measurements.
+	\end{itemize}
+
+	\section{Methods}
 
@@
 	\begin{itemize}
-		\item Initially parameterized monomer gives unfavorable structure
+          %MRS: this first about unfavorable structure not relevant - people will understand it needs to equilibrated/annealed.
+	  %BJC: But still talk about what I did to anneal it right?
+		\item Initially parameterized monomer gives unfavorable structure % Will delete this once I clarify the above comment
 		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
@@
 		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
-		%BJC: Openeye software to get the best charge for multiple configurations.
-		\item New configurations used for reparamaterization, BUT most likely will just use one set of charges for one configuration since I've done 90 percent of simulations based on one parameterization.
+		\item New configurations used for reparamaterization, BUT most likely will just use one set of charges from one configuration since I've done 90 percent of simulations based on one parameterization.
 In the future, I will have a single set of parameters.
+So, I have multiple configurations all with the same set of charges for now.
 	\end{itemize}
 
-	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable simulation length. 
+	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation. 
 	\begin{itemize}
@@
 		\end{itemize}  
-		\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
-		\item Code has adjustable parameters: Pore-to-Pore distance, pore radius, number of monomer layers (justification for parameters chosen in following paragraphs)
-		\item This is the thermotropic phase, information used depends on thermotropic experimental data
+		\item Wrote code to assemble monomers into Colh configuration (described in intro) close to what is expected 
+		\item Equilibration simulations allow structure to relax into expected configuration 
 	\end{itemize}
 
-        The validity of our model can be tested based on its agreement with experimental structural and material property data
-        \begin{itemize}
-                \item Our simulations should mimic the real system as best as we can within the limits imposed by choice of force field
-                \item Tougher with a large system for which no force fields have been specifically developed
-	\end{itemize}
-
-	After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
+	Twenty monomer layers per pore provides a balance of structural accuracy and computational efficiency. 
 	\begin{itemize}
@@
 
-	\noindent The remaining parameters were chosen based on experimental data. 
+        %MRS: A lot of these investigations probably belong in results, because they are answering the questions you have: what are the likely physical properties of these membranes?
+The parameters are actually variables you are investgating.
+	%BJC: Okay, condensed a couple paragraphs into one. I just want to explain here where the measurements came from and how 
+	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
 	\begin{itemize}
-		\item SAXS to get an idea of Pore-to-Pore
-		\begin{itemize}
-			\item multiple starting pore to pore distances tested (3.0, 3.5, 4.0, 4.5 nm)
-			\item 4.0 nm and 4.5 nm converged to similar dimensions, 4.5 nm was most reliable
-		\end{itemize}
+		\item SAXS gives an idea of Pore-to-Pore distances
 		\item TEM images and rejection give a pore size estimate
+		\item Ran long NPT simulations at 300 K and 1 bar ( > 200 ns )
 	\end{itemize}
 
-	\noindent NPT simulations were run at 300 K and 1 bar for system equilibration.
+        %MRS: Results of the crosslinking are likely in results -- the fact that it didn't really change the structure of the membrame. 
+	%BJC: Okay, then I will just give the gist of how I went about crosslinking and why I think it is the correct way to do it.
+	Using an equilibrated structure, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
 	\begin{itemize}
-		\item Monitored 'hexagonality' - i.e. how the distance between pores compares to an ideal hexagon
-		\item Varied initial pore-to-pore distance and ran very long simulations - typically > 200 ns
-	\end{itemize}
-
-	After an equilibrated structure was created, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
-	\begin{itemize}
-		\item Crosslinking maintains alignment of cylindrical mesophases
-		\item head to tail addition
-		\item racemic mixture 
-		\item Details of crosslinking algorithm (refer to appendix or supplemental info)
+		\item Crosslinking maintains alignment of cylindrical mesophases - emphasize that replicating the mechanism/kinetics is not important 
+		\item head to tail addition dominates so I only implemented that
+		\item racemic mixture - don't have to be too concerned about direction of attack 
+		\item Details of crosslinking algorithm (refer to appendix or supplemental info but give a brief overview here)
 	\end{itemize}
@@
 
-	A structurally accurate and reproducible model of the Colh phase LLC membrane has been developed
+	Proper selection of initial structural parameters results in an equilibrated model that is experimentally consistent 
 	\begin{itemize}
 		\item Visual perspective - show top view and cross section
-		\item System validated using multiple monomer configurations (working on this now)
+		\item System validated using multiple monomer configurations 
 		\item Pore to pore distance
@@
 			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
-			\item Effect of crosslinking
+			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
 		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
@@
 		\item Ions may play a role in transport, hindering flux of solute and solvent by slowing their diffusion
-		\item Experimentalists may be over-estimating the potential for high solvent flux through the pores because they view it as a hollow channel.
-The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes.
-%BJC: This seems dark and unencouraging but I think it's true.
-Maybe I shouldn't talk about it for now.
+		\item The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes. 
         \end{itemize}
@@
 
-	Our model can be used to evaluate other liquid crystalline assemblies
+%MRS: not really a result, but can be included in the discussion. Don't need to talk too much about future work though - a paper should be focused on the current work.
+%BJC: Okay, I'll be brief when writing this up
+	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies
 		\begin{itemize}
@@
 
-	In this work, a molecular model has been developed intended to predict transport in a thermotropic liquid crystal membrane. 
+        %MRS: restate in terms of the physical things learned.  THe output is knowledge, not a model.
+	In this work, we have revealed a more detailed picture of the structure of a self assembled thermotropic liquid crystal membrane using an atomistic molecular model.
+	%In this work, a molecular model has been developed intended to predict transport in a thermotropic liquid crystal membrane. 
 	\begin{itemize}
+		\item Channels are more disordered than previously thought
+		\item There are likely 6 or 7 monomers per layer (or somewhere in between if there is something like alternating layers)
 		\item Results presented for Colh phase monomer but can be adapted to other LCs

### 2017-01-20 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Added comments.

@@
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
+%MRS2: read over the start of the grant for more ideas about details for the motivation.
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
@@
 	% BJC - I think that this paragraph will not be included since we are not getting into mechansims at all
+        %MRS2: some of this is good motivation for WHY we care about the structure of the pore.  Without the structure, we
+        % can't understand the mechanism.
         A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
@@
 
+        %MRS2: correct, focus should be on the picture (the result) not the model (the means to obtain the result)
 	A clearer picture of the microscopic structure of LLC membranes, gained by building a molecular model, will change how we think about their design. 
@@
 			\item We can also test other, less simplistic arrangements - such as having alternating monomers per layer  %BJC: maybe leave mention of this out right and here and just address it in the results?
+       %MRS2: right.  Generally, you want to use the introduction to raise questions, not list everything you will do.
 		\end{itemize}
@@
 I also want to close off the conclusion since it should be a good segway into the Methods section.
+        %MRS2: fine for now.  I'll think about better phrasing as we go.
 	To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.
+
 	% Old thesis: A physically realistic molecular model with easily modified structural features will enable a qualitatively different type of membrane design aimed optimization of self assembled LLC membranes.
@@
 	  %BJC: But still talk about what I did to anneal it right? 
+          %MRS2: Yes.
 		\item Initially parameterized monomer gives unfavorable structure % Will delete this once I clarify the above comment
@@
 So, I have multiple configurations all with the same set of charges for now.
+%MRS2: now is the time to decide exactly what will be presented in the paper regarding alternative configurations/charges.
 	\end{itemize}
@@
 	Twenty monomer layers per pore provides a balance of structural accuracy and computational efficiency. 
+        %MRS2: describe quantitatively how you decided.  What is the information that made you make the decision?
 	\begin{itemize}
@@
 	The monomers are arranged into disks containing XXXX monomers in each layer. (Or are there defined layers -- I need to test this idea a bit more) 
+%MRS2: yes, examine this more. The idea of # of defined layers may be another idea to challenge. 
 	\begin{itemize}
@@
 	\end{itemize}
-
+%MRS2: Need to put into the outline how you quantitatively decided that layers wasnt meaningful.  Atom density as a function of Z, showed that it was uniform, not periodic? 
 	Sodium counterions are distributed randomly within the hydrophilic pore regions. (I should actually come up with a distribution e.g. gaussian) 
+%MRS2: right, there are many ways to be distributed randomly.
 	\begin{itemize}
@@
 		\item The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes. 
+%MRS2 good to get into the implied mechanism.
         \end{itemize}
@@
 %BJC: Okay, I'll be brief when writing this up
+%MRS2: or not even enumerate all the specific questions, just that it is a generalizable model.
 	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies
@@
         %MRS: restate in terms of the physical things learned.  THe output is knowledge, not a model.
-	In this work, we have revealed a more detailed picture of the structure of a self assembled thermotropic liquid crystal membrane using an atomistic molecular model.
+	In this work, we have 
+%MRS2: revealed 
+%MRS: revealed is too strong.
+suggested 
+a more detailed picture of the structure of a self assembled thermotropic liquid crystal membrane using an atomistic molecular model.
 	%In this work, a molecular model has been developed intended to predict transport in a thermotropic liquid crystal membrane. 
@@
 		\item Channels are more disordered than previously thought 
+                  %MRS2: not only disordered, but filled, rather than open.
 		\item There are likely 6 or 7 monomers per layer (or somewhere in between if there is something like alternating layers)
@@
 	\end{itemize}
+%MRS2: should this be in there you discussed in the email?
+%A crosslinked system to show that the system shrinks upon crosslinking as expected
+
+%MRS2: This is worth examining, in the paper, but ONLY if it gives
+%results like the X-ray diffraction shown earlier.  
+% A system with forced pi stacking (via the dipole method) could help us explain (or not) the missing peak in the wide angle data
+
+%MRS2: we should think about where new X-ray data  would go.
 

### 2017-01-23 Ben_Manuscripts/Paper1/Paper1_Outline.tex
updated with fixes and comments

@@
 The analysis used in this paper can be readily extended to the HII phase.
-                  %MRS: Doesn't the data appear to be that they are mostly the same in structure? Should address this to the extent we can.
-		  %BJC: They're structures are almost identical (same d100 plane spacing, monomer orientation) with the exception of water being present in the HII phase.
-I rephrased the last item to make that clearer.
 	\end{itemize}
@@
         % can't understand the mechanism.
-        A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
+	%BJC2: reworded the following thesis to focus it more in the structural direction
+        A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines for design of monomers used to create separation-specific membranes.
+	%A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
         \begin{itemize}
@@
 
-        %MRS2: correct, focus should be on the picture (the result) not the model (the means to obtain the result)
 	A clearer picture of the microscopic structure of LLC membranes, gained by building a molecular model, will change how we think about their design. 
@@
 			\item We can directly compare the plausibility of each situation along with other numbers of monomers per layer - 5, 6, 8
-			\item We can also test other, less simplistic arrangements - such as having alternating monomers per layer  %BJC: maybe leave mention of this out right and here and just address it in the results?
-       %MRS2: right.  Generally, you want to use the introduction to raise questions, not list everything you will do.
 		\end{itemize}
@@
 
-        %MRS: this is not the best way to phrase the thesis.
-I would say that we want to ask what the most likely features of the membrane are using molecular modeling.
-we can talk about the phrasing.
-But the model should not be the scientific output of the paper.
-	%BJC: Okay, tried again below, - basically what I want to communicate is that we want our model to tell us useful things and we can't do that unless we know that the model is realistic.
-We can have a good idea that it's realistic if we put thought into how we build it and if we can reproduce experimental results.
-I also want to close off the conclusion since it should be a good segway into the Methods section.
         %MRS2: fine for now.  I'll think about better phrasing as we go.
 	To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.
-
-	% Old thesis: A physically realistic molecular model with easily modified structural features will enable a qualitatively different type of membrane design aimed optimization of self assembled LLC membranes.
 	\begin{itemize}
@@
 	\begin{itemize}
-          %MRS: this first about unfavorable structure not relevant - people will understand it needs to equilibrated/annealed.
-	  %BJC: But still talk about what I did to anneal it right? 
-          %MRS2: Yes.
-		\item Initially parameterized monomer gives unfavorable structure % Will delete this once I clarify the above comment
 		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
 		\item Result not global minimum but close enough for structure building
+		\item Antechamber used for atomtyping with gaff forcefield
+		\item Used Openeye Quacpac molcharge.py to assign charges
+		\item Anneal again 
 		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
-		\item New configurations used for reparamaterization, BUT most likely will just use one set of charges from one configuration since I've done 90 percent of simulations based on one parameterization.
-In the future, I will have a single set of parameters.
-So, I have multiple configurations all with the same set of charges for now.
-%MRS2: now is the time to decide exactly what will be presented in the paper regarding alternative configurations/charges.
 	\end{itemize}
@@
 
-	Twenty monomer layers per pore provides a balance of structural accuracy and computational efficiency. 
+	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
+	%Twenty monomer layers per pore provides a balance of structural accuracy and computational efficiency. 
         %MRS2: describe quantitatively how you decided.  What is the information that made you make the decision?
+	%BJC2: It's hard to give much quantitative back up. We decided on this with more qualitative backup. We chose 20 to be safe but probably could have gotten away with less.
 	\begin{itemize}
@@
 
-        %MRS: A lot of these investigations probably belong in results, because they are answering the questions you have: what are the likely physical properties of these membranes?
-The parameters are actually variables you are investgating.
-	%BJC: Okay, condensed a couple paragraphs into one. I just want to explain here where the measurements came from and how 
 	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
@@
 
-        %MRS: Results of the crosslinking are likely in results -- the fact that it didn't really change the structure of the membrame. 
-	%BJC: Okay, then I will just give the gist of how I went about crosslinking and why I think it is the correct way to do it.
 	Using an equilibrated structure, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
@@
 %MRS2: yes, examine this more. The idea of # of defined layers may be another idea to challenge.
+%BJC2: I'd like to talk to you more about some calculations before I form a thesis. And that will guide the rest of this paragraph 
 	\begin{itemize}
@@
 %MRS2: Need to put into the outline how you quantitatively decided that layers wasnt meaningful.  Atom density as a function of Z, showed that it was uniform, not periodic? 
+%BJC2: working on it. It looks somewhat uniform. I'm trying to see what I can learn from the fourier transform
 	Sodium counterions are distributed randomly within the hydrophilic pore regions. (I should actually come up with a distribution e.g. gaussian) 

### 2017-01-24 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Responded to comments, added potential figure locations, started a supplementary info section

@@
 	\end{itemize}
+	FIGURE: initial configuration
+	caption: A representative initial configuration
 
@@
 			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
+			\item Simulated SAXS data
+		\end{itemize}
+		FIGURE - perhaps a four panel figure
+		(a) Experimental Small Angle X-ray scattering data
+		(b) Equilibration of pores monitored by measuring the distance between pores over time
+		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position 
+		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements  	
 		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
 		\item Density - there are crude lab measurements which my model is in agreement with (no one has reported any values since it wasn't relevant to them)
-		\end{itemize}
 	\end{itemize}
@@
                 \item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
+		\item Density of components along Z axis
+	        FIGURE: density of component along z axis (maybe FT for clarity)
+	        caption: The density of head groups along the axis parallel to the pores, as defined by the centroid of each benzene ring.
+There are no clear layers despite the defined layers in the starting configuration.
+
 	\end{itemize}
+
 %MRS2: Need to put into the outline how you quantitatively decided that layers wasnt meaningful.  Atom density as a function of Z, showed that it was uniform, not periodic? 
@@
 %MRS2: right, there are many ways to be distributed randomly.
+%BJC2: yes, I need to think about this more rather than assume gaussian
 	\begin{itemize}
@@
 		\item The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes.
-%MRS2 good to get into the implied mechanism.
+		FIGURE - plot from grant - sodium, benzene, tail densities in pores
+		caption: The density of sodium (blue), benzene (red), and alkyl tails (cyan) surrounding the membrane pore centers.
+The center of the pore is a soup of the three components as opposed to a previously assumed hollow region.
         \end{itemize}
+
+%BJC: New x-ray data here? It could potentially support the conclusions made in the previous paragraph.
 
@@
 	\end{itemize}
+	TABLE: Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion
 
@@
 %MRS2: or not even enumerate all the specific questions, just that it is a generalizable model.
+%BJC2: Okay, then is this even a paragraph? It could just be a final sentence or just moved to the conclusions
 	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies
@@
 
-        %MRS: restate in terms of the physical things learned.  THe output is knowledge, not a model.
-	In this work, we have 
-%MRS2: revealed 
-%MRS: revealed is too strong.
-suggested 
-a more detailed picture of the structure of a self assembled thermotropic liquid crystal membrane using an atomistic molecular model.
-	%In this work, a molecular model has been developed intended to predict transport in a thermotropic liquid crystal membrane. 
+	In this work, we have suggested a more detailed picture of the structure of a self assembled thermotropic liquid crystal membrane using an atomistic molecular model.
 	\begin{itemize}
-		\item Channels are more disordered than previously thought 
-                  %MRS2: not only disordered, but filled, rather than open.
-		\item There are likely 6 or 7 monomers per layer (or somewhere in between if there is something like alternating layers)
+		\item Channels are more disordered than previously thought and are filled with organic matter rather than being hollow 
+		\item There are likely no defined layers
 		\item Results presented for Colh phase monomer but can be adapted to other LCs
@@
 %A crosslinked system to show that the system shrinks upon crosslinking as expected
+%BJC2: It's included in the first paragraph of Results and Discussion & and proposed as part of a figure
 
@@
 % A system with forced pi stacking (via the dipole method) could help us explain (or not) the missing peak in the wide angle data
+%BJC2: would this go in a section about pitfalls of our model if it did prove show pi stacking. 
+%BJC2: It could also be used to refute the pi stacking argument for structuring of the pores if we show that it takes a large amount of energy to force it to even happen.
 
 %MRS2: we should think about where new X-ray data  would go.
+%BJC2: after where we talk about disordered pores?
 
+	\section{Supplemental Information}
+
+	Monomer configurations
+	\begin{itemize}
+		\item show all pore-to-pore equilibration plots used to prove independence of starting conifiguration
+		\item 3D visualizations of different configurations tested
+		\item 7 monomer per layer configurations
+	\end{itemize}
+
+	Crosslinking details
+	\begin{itemize}
+		\item Full algorithm? or just detailed description
+		\item Maybe a figure showing the new crosslinks
+	\end{itemize}
+
+	Ionic conductivity
+	\begin{itemize}
+		\item MSD plots
+	\end{itemize}
 \end{document}

### 2017-01-24 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updated
Responses to comments, fixes, started incorporating ideas for figures, added a supplemental info outline section

@@
 %MRS2: read over the start of the grant for more ideas about details for the motivation.
+%BJC2: Just noticed this comment before sending it back to you.
+I'll look at the grant again while editing the next iteration.
+I think I want to move away from framing the membrane as just a desalination membrane
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
@@
 		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII)
+		%BJC: this is making me scratch my head - I'm afraid to talk a lot about this because of Mike's new data. But I think it's important to distinguish between what has been reported in past literature 
 		\item The thermotropic, Colh is formed by the self assembly of neat monomer
-		\item The lyotropic, HII phase is formed in the presence of small percentages of water (around 8 percent)
+		\item The lyotropic, HII phase is formed in the presence of small amounts of water
 		\item Both assemble into cylinders with hydrophilic groups oriented inward towards the pore center and hydrophobic group facing outward.
@@
 	\begin{itemize}
-                \item Two types of self assembled LLCs have been made - thermotropic and lyotropic -- explain difference -- shift focus to Colh
+		\item Focus on Colh since it is a simpler system and has the same experimental data
 		\item Colh phase studies currently limited mostly to one monomer with minor variations
@@
 
-	A clearer picture of the microscopic structure of LLC membranes, gained by building a molecular model, will change how we think about their design. 
+	A clear picture of the microscopic structure of LLC membranes, gained by building a molecular model, will confirm or deny past drawn conclusions that have largely guided our understanding of separation mechanisms.
 	\begin{itemize}
@@
 
-	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation. 
+	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for more efficient way to build the system.
 	\begin{itemize}
@@
 	\end{itemize}
-	FIGURE: initial configuration
-	caption: A representative initial configuration
-
+	FIGURE: initial configuration \\
+	caption: A representative initial configuration \\
+	\\
 	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
@@
 	\begin{itemize}
-		\item Visual perspective - show top view and cross section
+		\item Visual perspective \\
+		FIGURE: show top view and cross section (with pbcs on)\\
+		caption: (a) A top view of an equilibrated LLC membrane system shows defined pores and the expected hexagonal morphology. \\
+		(b) A side vew of an equilibrated LLC membrane system shows the straight cylindrical pores, emphasized by large blue sodium ions 
 		\item System validated using multiple monomer configurations 
@@
 		FIGURE - perhaps a four panel figure
-		(a) Experimental Small Angle X-ray scattering data
-		(b) Equilibration of pores monitored by measuring the distance between pores over time
-		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position 
-		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements  	
+		(a) Experimental Small Angle X-ray scattering data \\
+		(b) Equilibration of pores monitored by measuring the distance between pores over time \\
+		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\ 
+		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\  	
 		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
@@
 		\item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
-		\item Density of components along Z axis
+		\item Density of components along Z axis \\
 		FIGURE: density of component along z axis (maybe FT for clarity)
@@
 		\item The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes.
-		FIGURE - plot from grant - sodium, benzene, tail densities in pores
+		\\FIGURE - plot from grant - sodium, benzene, tail densities in pores
 		caption: The density of sodium (blue), benzene (red), and alkyl tails (cyan) surrounding the membrane pore centers.
@@
 	TABLE: Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion
-
+	\\
 	%MRS: not really a result, but can be included in the discussion. Don't need to talk too much about future work though - a paper should be focused on the current work.
@@
 
-	Crosslinking details
+	\noindent Crosslinking details
 	\begin{itemize}
@@
 
-	Ionic conductivity
+	\noindent Ionic conductivity
 	\begin{itemize}

### 2017-01-27 Ben_Manuscripts/Paper1/Paper1_Outline.tex
updated outline.

@@
 I think I want to move away from framing the membrane as just a desalination membrane
+%MRS3: I agree - desalination is one possible use, but its more about transport / structure in general.
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
@@
 			\item Does concentration of ions in the pore repel incoming ions?
+               %MRS3: add potential reasons for transport  about non-ionic solutes as well.           
 		\end{itemize}
@@
 		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
+                  %MRS3 rewrite next line to reflect how the thesis will be stated in the paper.
 		\item There is no clear answer in literature defining what that set number of monomers is. I'd like to confirm or deny past predictions
@@
 
-	%MRS2: fine for now.  I'll think about better phrasing as we go.
+	%MRS3: Take a pass at reprhasing this -- important to get this right. don't start with a preposition.
+
 	To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.
@@
 		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
-		\item Small number of layers create micellar structure
+		\item Small number of layers create micellar structure %MRS3: specify.
 		\item Beyond 20 layers is unnecessary to get expected configuration
@@
 	\end{itemize}
+%MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
 	FIGURE: initial configuration \\
@@
 		\item TEM images and rejection give a pore size estimate
-		\item Ran long NPT simulations at 300 K and 1 bar ( > 200 ns )
+		\item Ran long NPT simulations at 300 K and 1 bar ( $>$200 ns )
 	\end{itemize}
@@
 		\item Visual perspective \\
+%MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
 		FIGURE: show top view and cross section (with pbcs on)\\
@@
 		\item System validated using multiple monomer configurations 
+                  %MRS3: be mroe precise what ``validation'' means.
 		\item Pore to pore distance
@@
 		\end{itemize}
+                %MRS3: see above on putting in thesis and what you are trying to convince readers.
 		FIGURE - perhaps a four panel figure
@@
 	%BJC2: I'd like to talk to you more about some calculations before I form a thesis. And that will guide the rest of this paragraph 
+        %MRS3: great, we'll talk tomorrow.
+If it is disordered, then there are two kinds of disorder people weren't really talking about -- disorder in the z direction, and disorder in the radial direction.
 	\begin{itemize}
@@
 		\item It has been suggested that there are 4 monomers in a each disk/layer, however, simulations have shown that this leads to unstable configurations with dimensions that are too small compared to experiment.
+%MRS3: write as it will appear in the paper.  Add ``will be done'' notes in comments.
 		\item Stable simulations with 6 and 7 monomers have been performed (will do one with five soon) which give structural characteristics consistent with experiment
@@
 		caption: The density of head groups along the axis parallel to the pores, as defined by the centroid of each benzene ring. 
+%MRS3: aha, this here below is a thesis, something you are convincing the reader is true.
 There are no clear layers despite the defined layers in the starting configuration.
@@
 		\\FIGURE - plot from grant - sodium, benzene, tail densities in pores
+                %MRS3: again, thesis.
 		caption: The density of sodium (blue), benzene (red), and alkyl tails (cyan) surrounding the membrane pore centers.
@@
 	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies
+        %MRS3: I don't think we really need to explore all the other possibilities - just that it allows for design of new nanoporous membranes. 
 	\begin{itemize}
@@
 		\item Model can be used for prediction of transport properties in new membranes
+%MRS3: probably don't need to talk about this, since we don't present these results.
 		\item We will solvate the system to establish procedures for HII phase prediction
@@
 	%BJC2: after where we talk about disordered pores?
-
+        %MRS3: sure, sounds good.   LEt's talk about what resolution on pores we can get from simulation.	
 	\section{Supplemental Information}
@@
 		\item 3D visualizations of different configurations tested
-		\item 7 monomer per layer configurations
+		\item 7 monomer per layer configurations  %MRS3: and others if needed.
 	\end{itemize}
@@
 	\begin{itemize}
+          %MRS3: we can decide, but enough detail to replicate.  Should have the code in a repository that can be distributed.
 		\item Full algorithm? or just detailed description
-		\item Maybe a figure showing the new crosslinks
+		\item Maybe a figure showing the new crosslinks %MRS3: yes.
 	\end{itemize}
 
-	\noindent Ionic conductivity
+	\noindent Ionic conductivity % plus more details on implementation.
 	\begin{itemize}

### 2017-01-28 Ben_Manuscripts/Paper1/Paper1_Outline.tex
editing outline

@@
 		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
-		\item Small number of layers create micellar structure %MRS3: specify.
+		\item 5 layers create micellar structure %MRS3: specify.
 		\item Beyond 20 layers is unnecessary to get expected configuration
@@
 %MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
+%BJC3: Maybe i include this in the supplemental information. I don't think a picture of the initial configuration is actually that interesting or important 
 	FIGURE: initial configuration \\
@@
 %MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
-		FIGURE: show top view and cross section (with pbcs on)\\
-		caption: (a) A top view of an equilibrated LLC membrane system shows defined pores and the expected hexagonal morphology. \\
-		(b) A side vew of an equilibrated LLC membrane system shows the straight cylindrical pores, emphasized by large blue sodium ions 
+		FIGURE: shows top view and cross section (with pbcs on)\\
+		%caption: (a) A top view of an equilibrated LLC membrane system shows defined pores and the expected hexagonal morphology. \\
+		%(b) A side vew of an equilibrated LLC membrane system shows the straight cylindrical pores, emphasized by large blue sodium ions 
+			caption: % BJC3: Attempt #2 trying to make it more thesis like. These aren't meant to do much other than show that we get, qualitatively, the same strucure described in the literature
+		(a) The expected hexagonal membrane morphology is preserved upon equilibration
+		(b) Straight cylindrical pore regions are present 
 		\item System validated using multiple monomer configurations 

### 2017-02-16 Ben_Manuscripts/Paper1/Paper1_Outline.tex
updated outline
Drew some ideas from the DMREF proposal for the intro. There are still some ambiguous parts which I am working to answer right now.

@@
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-%MRS2: read over the start of the grant for more ideas about details for the motivation.
-%BJC2: Just noticed this comment before sending it back to you.
-I'll look at the grant again while editing the next iteration.
-I think I want to move away from framing the membrane as just a desalination membrane
-%MRS3: I agree - desalination is one possible use, but its more about transport / structure in general.
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
@@
 	\section{Introduction}
-	Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
+	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale.
 	\begin{itemize}
@@
 		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
+		\item Designing RO membranes to achieve targeted separations of specific solutes is nearly impossible due to the separation (hypothesized to be) controlled by fluctuating polymer voids
+		\item RO has difficulty separating neutral organics because they tend to dissolve in polymer matrix
+		\item Many current RO membranes degrade in typical chlorine filled municipal water supplies (debating this point because there aren't any studies of LLC membrane fouling resistance)  
 		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
+		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
+		\item Entirely different mechanisms govern the separation processes in various nano structured materials which can inspire novel separation techniques
 	\end{itemize}
@@
 		\begin{itemize}
-			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
+			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact 
 			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
+			%BJC: The following are ideas pulled from the grant. I need to do some reserach and come up with some one liners as to why each have not been successful
+			\item Track-etch membranes
+		    \item Molecular squares
+			\item Macrocyclic surfactants 
 		\end{itemize}
 	\end{itemize}
+
 	Self assembling lyotropic liquid crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques feasible for large scale production.
 	\begin{itemize}
-		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
-		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII)
+		\item LLCs are versatile and controllable with a large chemical design space available for membrane design
+		\item Synthetic techniques are cheap and amenable to creating any monomer in this large design space
+		\item LLCs forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
+		\item Na-GA3C11 forms two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII)
 		%BJC: this is making me scratch my head - I'm afraid to talk a lot about this because of Mike's new data. But I think it's important to distinguish between what has been reported in past literature 
-		\item The thermotropic, Colh is formed by the self assembly of neat monomer
+		\item The thermotropic, Colh, is formed by the self assembly of neat monomer
 		\item The lyotropic, HII phase is formed in the presence of small amounts of water
@@
 		\item Until recently, they could not be aligned - hindered progress
-		\item Yale aligns them, then crosslinks them to lock in the structure
+		\item Yale aligns them, then crosslinks them to lock in the structure - reference 2014 and 2016 papers
 		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
@@
 
-	% BJC - I think that this paragraph will not be included since we are not getting into mechansims at all
-	%MRS2: some of this is good motivation for WHY we care about the structure of the pore.  Without the structure, we
-	% can't understand the mechanism.
-	%BJC2: reworded the following thesis to focus it more in the structural direction
 	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines for design of monomers used to create separation-specific membranes.
-	%A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
 	\begin{itemize}
-		\item Focus on Colh since it is a simpler system and has the same experimental data
-		\item Colh phase studies currently limited mostly to one monomer with minor variations
-		\item Current optimization efforts performed through trial and error
-		\item Macroscopic models are the only source of predictive modeling
+		\item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effect water desalination and small organic separations.
+Rejection studies show that this membrane can't do desalination
+		\item We can create a molecular model that will give us the desired understanding
+		\item Our focus is on Colh since it is a simpler system and has the same experimental data
+		\item Colh phase studies currently limited mostly to one monomer
+		\item Optimization efforts performed through trial and error
+		\item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
 		\item An atomistic understanding of the mechanism of solute transport can identify
@@
 			\item Does concentration of ions in the pore repel incoming ions?
-               %MRS3: add potential reasons for transport  about non-ionic solutes as well.           
+			\item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection
+			\item Is water structured inside the pores leading to transport barriers?  
 		\end{itemize}
@@
 		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
-                  %MRS3 rewrite next line to reflect how the thesis will be stated in the paper.
-		\item There is no clear answer in literature defining what that set number of monomers is. I'd like to confirm or deny past predictions
-		\begin{itemize}
 		\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
-			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer
-			\item We can directly compare the plausibility of each situation along with other numbers of monomers per layer - 5, 6, 8
-		\end{itemize}
+		\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each 
+		\item We can use fourier analysis to determine if there are distinct layers, and if so, how many monomers are situated in each layer.
 	\end{itemize}
@@
 
-	To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.
+	We must show that the developed molecular model is physically realistic so that we can trust conclusions drawn about structural features characteristic of the system.
+	%old:To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.
 	\begin{itemize}
@@
 		\item We are primarily interested in reproducing the conclusions about structure which can be made from SAXS experiments, predicting ionic conductivity with a reasonable comparison to experiment, and reproducing experimental density measurements.
+			\item We can simulate x ray diffraction patterns based on atomic coordinates
+			\item We can predict ionic conductivity using two agreeing methods
+			\item Density? - I will ask Mike to take more density measurements. It seems worthwhile     
 	\end{itemize}
@@
 
-	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for more efficient way to build the system.
+	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for a more efficient way to build the system.
 	\begin{itemize}
-		\item Work done that shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
+		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
 		\item Attempts with Colh system not fruitful  
@@
 			\item Packed monomers into box
-			\item Simulated for ~100 ns with no real progress shown towards self assembly
+			\item Simulated for ~100 ns with no progress shown towards self assembly
 		\end{itemize}  
-		\item Wrote code to assemble monomers into Colh configuration (described in intro) close to what is expected 
+		\item Wrote code to assemble monomers into Colh configuration close to what is expected 
 		\item Equilibration simulations allow structure to relax into expected configuration 
@@
 	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
-	%Twenty monomer layers per pore provides a balance of structural accuracy and computational efficiency. 
+	%Twenty monomer  per pore provides a balance of structural accuracy and computational efficiency. 
 	%MRS2: describe quantitatively how you decided.  What is the information that made you make the decision?
@@
 		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
-		\item 5 layers create micellar structure %MRS3: specify.
+		\item 5 layers create micellar structure
 		\item Beyond 20 layers is unnecessary to get expected configuration
@@
 %MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
-%BJC3: Maybe i include this in the supplemental information. I don't think a picture of the initial configuration is actually that interesting or important 
+%BJC3: Maybe i include this in the supplemental information.
+I don't think a picture of the initial configuration is actually that interesting or important.
+I can't think of a thesis for a figure that is purely illustrative
 	FIGURE: initial configuration \\
-	caption: A representative initial configuration \\
+	caption: A representative initial configuration. The pores are rotated to prevent overlaps \\
 	\\
@@
 		\item SAXS gives an idea of Pore-to-Pore distances
-		\item TEM images and rejection give a pore size estimate
-		\item Ran long NPT simulations at 300 K and 1 bar ( $>$200 ns )
+		\item TEM images and rejection studies give a pore size estimate
+		\item To prevent unrealistic jumps during initial equilibration steps, the following equilibration scheme was adopted
+			\begin{itemize}
+			\item Apply position restraints to monomer head groups during energy minimization 
+			\item Leave position restraints for npt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
+			\item Gradually reduce force constants (by square root every 50 ps) until they are completely off
+			\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate
+			\end{itemize}
 	\end{itemize}
@@
 		(b) Straight cylindrical pore regions are present 
-		\item System validated using multiple monomer configurations 
-                  %MRS3: be mroe precise what ``validation'' means.
+		\item System dimensions and properties are consistent upon equilibration using multiple monomer configurations 
 		\item Pore to pore distance
@@
 		\end{itemize}
-                %MRS3: see above on putting in thesis and what you are trying to convince readers.
 		FIGURE - perhaps a four panel figure
-		(a) Experimental Small Angle X-ray scattering data \\
-		(b) Equilibration of pores monitored by measuring the distance between pores over time \\
+		(a) Experimental Small Angle X-ray scattering data shows confirms a hexagonally packed morphology and tells us the distance between pores \\
+		(b) Measuring the distance between pores over time indicates equilibration when the distances stop changing \\
 		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\ 
@@
 
-	The monomers are arranged into disks containing XXXX monomers in each layer. (Or are there defined layers -- I need to test this idea a bit more) 
-	%MRS2: yes, examine this more. The idea of # of defined layers may be another idea to challenge.
-	%BJC2: I'd like to talk to you more about some calculations before I form a thesis. And that will guide the rest of this paragraph 
-        %MRS3: great, we'll talk tomorrow.
-If it is disordered, then there are two kinds of disorder people weren't really talking about -- disorder in the z direction, and disorder in the radial direction.
+	The monomers are arranged into disks containing 5 monomers in each layer.
+	%BJC: So, it looks like there is some kind of z directional order
+
 	\begin{itemize}
-		\item Hypothesis: There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature.
-While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains.
-Staying completely ordered, stacked on top of each other is not entropically favorable.
 		\item It has been suggested that there are 4 monomers in a each disk/layer, however, simulations have shown that this leads to unstable configurations with dimensions that are too small compared to experiment.
-%MRS3: write as it will appear in the paper.  Add ``will be done'' notes in comments.
-		\item Stable simulations with 6 and 7 monomers have been performed (will do one with five soon) which give structural characteristics consistent with experiment
+		\item Stable simulations with 6 and 7 monomers have been performed which give structural characteristics consistent with experiment
 		\item Stable systems have also been simulated consisting of varying numbers of monomers per layer
+		\item Calculating the number density of components in the z direction has shown defined groups % will do for 7 monomers / layer and alternating monomers / layer
+		\\ Figure \\
+		(a) The number density of benzene ring centers in the z direction shows regions with higher concentrations of the component \\
+		(b) A power spectrum of the data in (a) indicates that a new layer is defined every 4 angstroms implying that there are 5 monomers per layer.\\
+		\item Even though there are defined regions of higher component density, there is still considerable variation in the position of the components (shown by the extra noise in the power spectrum)
 		\item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
 		\item Density of components along Z axis \\
-		FIGURE: density of component along z axis (maybe FT for clarity)
-		caption: The density of head groups along the axis parallel to the pores, as defined by the centroid of each benzene ring. 
-%MRS3: aha, this here below is a thesis, something you are convincing the reader is true.
-There are no clear layers despite the defined layers in the starting configuration.
+		\item There are not clear layers despite the defined layers in the starting configuration.
 
@@
 
-	%MRS2: Need to put into the outline how you quantitatively decided that layers wasnt meaningful.  Atom density as a function of Z, showed that it was uniform, not periodic? 
-	%BJC2: working on it. It looks somewhat uniform. I'm trying to see what I can learn from the fourier transform
-	Sodium counterions are distributed randomly within the hydrophilic pore regions. (I should actually come up with a distribution e.g. gaussian) 
-	%MRS2: right, there are many ways to be distributed randomly.
-	%BJC2: yes, I need to think about this more rather than assume gaussian
+	The arrangement of sodium counterions within the hydrophilic pore regions can be fit to a gaussian distribution. 
 	\begin{itemize}
@@
                 %MRS3: again, thesis.
-		caption: The density of sodium (blue), benzene (red), and alkyl tails (cyan) surrounding the membrane pore centers.
-The center of the pore is a soup of the three components as opposed to a previously assumed hollow region.
+		caption: The densities of sodium (blue), benzene (red), and alkyl tail carbons (cyan) surrounding the membrane pore centers indicate that each the pore region is a soup of the three components opposing the previously assumed hollow region.
 	\end{itemize}
 
-	%BJC: New x-ray data here? It could potentially support the conclusions made in the previous paragraph.
+	%BJC: New x-ray data here. Need higher resolution simulated data (working on it) and supporting experimental results first.
 
@@
 	\end{itemize}
-	TABLE: Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion
+	TABLE: Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error
 	\\
-	%MRS: not really a result, but can be included in the discussion. Don't need to talk too much about future work though - a paper should be focused on the current work.
-	%BJC: Okay, I'll be brief when writing this up
-	%MRS2: or not even enumerate all the specific questions, just that it is a generalizable model.
-	%BJC2: Okay, then is this even a paragraph? It could just be a final sentence or just moved to the conclusions
-	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies
-        %MRS3: I don't think we really need to explore all the other possibilities - just that it allows for design of new nanoporous membranes. 
-	\begin{itemize}
-		\item Liquid crystal used - or a mixture of different liquid crystals
-		\item Minor structural variations (e.g. 7, 8, 9, 10, 11 ... CH2's in the tails)
-		\item Counterion -- Size/valence of counterion
-		\item Functional head groups
-		\item How does varying these things effect pore separation, pore size, phase stability, and transport and why are these effects observed
-	\end{itemize}
+
+	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies.
+Using the design framework and analysis methods applied herin, we have the ability to reliably predict properties of new nanoporous membranes.
 
@@
 	\begin{itemize}
-		\item Channels are more disordered than previously thought and are filled with organic matter rather than being hollow 
+		\item The model's physical properties are consistent with experimental measurements
+		\item Channels are more disordered than previously thought and are filled with organic matter rather than hollow 
 		\item There are likely no defined layers
-		\item Results presented for Colh phase monomer but can be adapted to other LCs
-		\item Model can be used for prediction of transport properties in new membranes
-%MRS3: probably don't need to talk about this, since we don't present these results.
-		\item We will solvate the system to establish procedures for HII phase prediction
+		\item Results presented for Colh phase monomer but methods are readily adapted to other LCs
 	\end{itemize}
-	%MRS2: should this be in there you discussed in the email?
-	%A crosslinked system to show that the system shrinks upon crosslinking as expected
-	%BJC2: It's included in the first paragraph of Results and Discussion & and proposed as part of a figure
 
-	%MRS2: This is worth examining, in the paper, but ONLY if it gives
-	%results like the X-ray diffraction shown earlier.  
-	% A system with forced pi stacking (via the dipole method) could help us explain (or not) the missing peak in the wide angle data
-	%BJC2: would this go in a section about pitfalls of our model if it did prove show pi stacking. 
-	%BJC2: It could also be used to refute the pi stacking argument for structuring of the pores if we show that it takes a large amount of energy to force it to even happen.
-
-	%MRS2: we should think about where new X-ray data  would go.
-	%BJC2: after where we talk about disordered pores?
-        %MRS3: sure, sounds good.   LEt's talk about what resolution on pores we can get from simulation.	
 	\section{Supplemental Information}
@@
 		\item 3D visualizations of different configurations tested
-		\item 7 monomer per layer configurations  %MRS3: and others if needed.
+		\item 7 monomer per layer configurations and others if needed.
 	\end{itemize}
@@
 	\begin{itemize}
-          %MRS3: we can decide, but enough detail to replicate.  Should have the code in a repository that can be distributed.
-		\item Full algorithm? or just detailed description
-		\item Maybe a figure showing the new crosslinks %MRS3: yes.
+		\item Algorithm description. Link to full algorithm in git repository
+		\item A figure showing the new crosslinks
 	\end{itemize}

### 2017-02-20 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Update outline.

@@
 	%MRS3: Take a pass at reprhasing this -- important to get this right. don't start with a preposition.
-
+        %MRS4: maybe ``consistent with physical observations?''
 	We must show that the developed molecular model is physically realistic so that we can trust conclusions drawn about structural features characteristic of the system.
@@
 	%BJC2: It's hard to give much quantitative back up. We decided on this with more qualitative backup. We chose 20 to be safe but probably could have gotten away with less.
+        %MRS4: OK, but note that we will need to expand this to be enough convincing qualitative information.
+Could also use quantitaitve information about how far from the surface you see the effects of the surface.
 	\begin{itemize}
@@
 	FIGURE: initial configuration \\
+%MRS4: I'm not quite sure what ``pores are rotated'' means.
 	caption: A representative initial configuration. The pores are rotated to prevent overlaps \\
@@
 
-	Proper selection of initial structural parameters results in an equilibrated model that is experimentally consistent 
+	Proper selection of initial structural parameters results in an equilibrated model that is 
+%MRS4: change to be more specific.
+consistent with several key experimental measurements.
+%experimentally consistent 
 	\begin{itemize}
@@
 		\end{itemize}
+%MRS4: seems like an awful lot to put into one figure, even with multiple panels.
 		FIGURE - perhaps a four panel figure
@@
 		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\
+%MRS4: I think we will need to be much more specific about how the simulated x-ray diffraction pattern matches experimental masurement, and the different features that do match.  	
 		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
@@
 		(b) A power spectrum of the data in (a) indicates that a new layer is defined every 4 angstroms implying that there are 5 monomers per layer.\\
+%MRS4: make it clear that this is calculated from the equilbrium distance. 
+%MRS5: in general, there should be some information we can see looking directly at the density, not just the power spectrum.  We will need to convince people there is something there.
 		\item Even though there are defined regions of higher component density, there is still considerable variation in the position of the components (shown by the extra noise in the power spectrum)
@@
 		\item Density of components along Z axis \\
+%MRS4: we need to reconcile the idea ``there are 5 monomers per layer'' and ``there are not clear layers''.  It will be hard for me to reconcile them without knowing a bit more information.
+%MRS4: question: are the monomers themselves in a helical shape (not just the head groups?)
 		\item There are not clear layers despite the defined layers in the starting configuration.
@@
                 %MRS3: again, thesis.
+%MRS4: we should think a little bit about whether which parts of the alkyl tail we plot, and whether to just focus on the core (ignoring the first 5 A or so from each end).
+Depends on what we are trying to show.
 		caption: The densities of sodium (blue), benzene (red), and alkyl tail carbons (cyan) surrounding the membrane pore centers indicate that each the pore region is a soup of the three components opposing the previously assumed hollow region.
@@
 	%BJC: New x-ray data here. Need higher resolution simulated data (working on it) and supporting experimental results first.
+        %MRS4 got it.  Will need to do some work on making this clear.
 
@@
 		\item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system
+                %MRS4: not sure you describe how to do that here.
 		\item Two methods used to for prediction

### 2017-03-07 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updated outline with plan for experiments involving various configurations

@@
 
-	%MRS3: Take a pass at reprhasing this -- important to get this right. don't start with a preposition.
-        %MRS4: maybe ``consistent with physical observations?''
-	We must show that the developed molecular model is physically realistic so that we can trust conclusions drawn about structural features characteristic of the system.
-	%old:To trust our understanding of which structural features are most likely characteristic of the system, and the conclusions drawn thereof, we must show that our molecular model is physically realistic.
+	We must show that the developed molecular model is consistent with physical observations so that we can trust conclusions drawn about structural features characteristic of the system.
 	\begin{itemize}
@@
 	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
-	%Twenty monomer  per pore provides a balance of structural accuracy and computational efficiency. 
-	%MRS2: describe quantitatively how you decided.  What is the information that made you make the decision?
-	%BJC2: It's hard to give much quantitative back up. We decided on this with more qualitative backup. We chose 20 to be safe but probably could have gotten away with less.
         %MRS4: OK, but note that we will need to expand this to be enough convincing qualitative information.
@@
 		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
+		\item How far into membrane do we have to go to avoid effects of the surface (this is a TODO)
 	\end{itemize}
@@
 	FIGURE: initial configuration \\
-%MRS4: I'm not quite sure what ``pores are rotated'' means.
-	caption: A representative initial configuration. The pores are rotated to prevent overlaps \\
+	caption: A representative initial configuration. Each pore is rotated about the z axis rotated to prevent overlaps between pores \\
 	\\
@@
 
-	Proper selection of initial structural parameters results in an equilibrated model that is 
-%MRS4: change to be more specific.
-consistent with several key experimental measurements.
-%experimentally consistent 
+	Appropriate selection of initial structural parameters including interlayer spacing, relative interlayer orientation, and pore spacing results in an equilibrated model that is experimentally consistent.
 	\begin{itemize}
@@
 		FIGURE: shows top view and cross section (with pbcs on)\\
-		%caption: (a) A top view of an equilibrated LLC membrane system shows defined pores and the expected hexagonal morphology. \\
-		%(b) A side vew of an equilibrated LLC membrane system shows the straight cylindrical pores, emphasized by large blue sodium ions 
-			caption: % BJC3: Attempt #2 trying to make it more thesis like. These aren't meant to do much other than show that we get, qualitatively, the same strucure described in the literature
-		(a) The expected hexagonal membrane morphology is preserved upon equilibration
-		(b) Straight cylindrical pore regions are present 
+		caption: \\ 
+		(a) The expected hexagonal membrane morphology is preserved upon equilibration \\
+		(b) Straight cylindrical pore regions are present \\
 		\item System dimensions and properties are consistent upon equilibration using multiple monomer configurations 
@@
 			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
-			\item Simulated SAXS data
 		\end{itemize}
-%MRS4: seems like an awful lot to put into one figure, even with multiple panels.
-		FIGURE - perhaps a four panel figure
-		(a) Experimental Small Angle X-ray scattering data shows confirms a hexagonally packed morphology and tells us the distance between pores \\
-		(b) Measuring the distance between pores over time indicates equilibration when the distances stop changing \\
-		(c) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\ 
-		(d) A simulated x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\
-%MRS4: I think we will need to be much more specific about how the simulated x-ray diffraction pattern matches experimental masurement, and the different features that do match.  	
+
+		FIGURE - 2 panels \\
+		(a) Measuring the distance between pores over time indicates equilibration when the distances stop changing \\
+		(b) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\
+
+		\item Simulated X-ray Diffraction
+		\begin{itemize}
+			\item We used the 3 dimensional fourier transformed electron density to generate simulated 1D and 2D diffraction patterns
+			\item The 1D patterns are generated by spherical integration of the FT
+			\item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
+			\item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
+		\end{itemize}
+
+		FIGURE - 4 panels \\
+        	(a) Experimental Small Angle X-ray Scattering data confirms a hexagonally packed morphology and tells us the average distance between pores \\
+        	(b) A simulated 1D x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\
+        	(c) Experimental Wide Angle X-ray Scattering patterns provide details of structure on a length scale less than 1 nm.
+The diffuse ring at q = 1.4 A\textsuperscript{-1} represents the average distance between carbons in packed alkyl chains.
+Meridional reflections at q = TBD A\textsuperscript{-1} are caused by pi-stacking.
+The weak meridional reflections at q = TBD A\textsuperscript{-1} are hypothesized to be a consequence of parallel-displaced stacking of benzene rings \\
+		(d) Simulated X-ray diffraction pattern show the same dominant reflections which appear experimentally
+
 		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
@@
 
+        Experiments to be run!
+        \begin{itemize}
+                   \item Layered vs. offset configuration
+                   \begin{itemize}
+                        \item All simulations involving 'offset' configurations (which seems to be the correct configuration) will have a 'layered' counterpart in order to highlight difference between the two configurations.
+                        \item The comparison can be a figure in supplemental information
+                   \end{itemize}
+                   \item Measures of stability / analysis (These methods will be applied to all simulations run)
+                   \begin{itemize}
+                        \item Pore-to-pore distances
+                        \item Tilt angle vs. time
+                        \item Radial distribution functions
+                        \item Simulated diffraction patterns
+                   \end{itemize}
+                   \item Effect of temperature on stability of configurations
+                   \begin{itemize}
+                        \item Three different temperature systems have been set up and simulated for 20 ns (All with 20 layers and no vapor gap): 260K, 280K and 300K
+                        \item I have systems with no restraints on at all three temperatures
+                        \item We can look at them with weak restraints in case the systems misbehave as time goes on. As of now, the tilt angles look to stabilize after 10 ns
+                        \item If we get stable configurations with correct XRD patterns at lower temps but not higher, it may be a consequence of the forcefield
+                        \end{itemize}
+                   \item Effect of restraints on stability
+		   \begin{itemize}
+                        \item Run out simulations with weak restraints (f = 0.1 kJ/mol*nm2)
+                        \item Higher restraints may cause the system to be too ordered, but it may be worth running in the case of long term movement
+                        \item Run out simulations with no restraints (same simulation as 300K, no restraints from temperature stability sims)
+                        \item Hopefully this will let us abandon restraints after equilibration
+                   \end{itemize}
+		   \item Other simulations
+                   \begin{itemize}
+                        \item Offset, no vapor gap, 20 layer : No tilt (i.e.
+use monomers that I have previously used).
+I want to see if the diagonal spots still show up.
+The concern here is that I wont be able to get the monomers close enough together without causing some unreconcilable energy minimization errors.
+                        \item Offset, higher tilt.
+I'm working on a monomer that tilted more than the one I previously used.
+Can I make spots appear based purely on tilt?
+Also, what implications does this have for the pore spacing.
+                   \end{itemize}
+        \end{itemize}
+
 	The monomers are arranged into disks containing 5 monomers in each layer.
 	%BJC: So, it looks like there is some kind of z directional order 
+       	%BJC5: This will require some re-evaluation once we come to a reliable starting configuration and equilibration procedure based on the diffraction results
 
@@
 %MRS4: we need to reconcile the idea ``there are 5 monomers per layer'' and ``there are not clear layers''.  It will be hard for me to reconcile them without knowing a bit more information.
-%MRS4: question: are the monomers themselves in a helical shape (not just the head groups?)
+%BJC5: Hopefully I'll have an answer to this soon. For now I'm leaving it untouched
 		\item There are not clear layers despite the defined layers in the starting configuration.
@@
                 %MRS4: not sure you describe how to do that here.
+		%BJC5: We should discuss how we will actually make the link.
+We talked about it once but kind of left it hanging.
+It will likely be just some constant that we multiply our number by.
+To calculate the constant, I think using the azimuthal distribution is a good way to go about it.
+Although for that we'd need more data points telling us ionic conductivity as a function of azimuthal angle.
+That data will definitely be hard to come by in the near future so maybe a linear model is an okay estimate for now -- just to have something.
+For that, we know ionic conductivity with randomly oriented crystalline domains and we know ionic conductivity of a 'perfectly' aligned system (from our simulations).
+So we can make ionic conductivity as a linear function of alignment, I(x) (Actually it'd be piecewise with opposite slopes on either side of the an azimuthal angle of 90).
+Then we can integrate the azimuthal distribution weighted by I(x) to get a number to multiply our measurements by.
 		\item Two methods used to for prediction

### 2017-03-08 Ben_Manuscripts/Paper1/Paper1_Outline.tex
updated feedback with MRS4

@@
         Experiments to be run!
+%MRS4: more generally, we may want to explore the fact that there are other stable configurations (like the disordered ones we have found).
+We should brainstorm ways of calculating the free energy difference, BUT we should avoid it in this paper.
         \begin{itemize}
@@
                         \item All simulations involving 'offset' configurations (which seems to be the correct configuration) will have a 'layered' counterpart in order to highlight difference between the two configurations.
+%MRS4: Which, hopefully, will show that that is not consistent with experiment.
                         \item The comparison can be a figure in supplemental information
@@
                         \item Pore-to-pore distances
-                        \item Tilt angle vs. time
-                        \item Radial distribution functions
+                        \item Tilt angle vs. time  % it seems more likely that the circular anisotropy is NOT tilt angle but it is worth monitoring for now.
+                        \item Radial distribution functions  %MRS: this may be some thing that we present as an analysis AFTER we look at stability, since the other things are more things that can be verified vs.
+experiment.
                         \item Simulated diffraction patterns
                    \end{itemize}
-                   \item Effect of temperature on stability of configurations
+                   %MRS4: so this is something that we want to be careful about how we present the rationale.
+THe original rationale is that if the interactions were effectively too weak compared to experiemnt, then the 'effective' temperature would be a bit higher than we the 'thermostatted' temperature.
+I think that
+                   \item Effect of temperature on stability of configurations.
+15 degrees off (room temperature is 295) is much more likely than 260, though for our purposes, we probably want to run lower just to be sure.
+Would be interesting to know the temperature stability of the experimental structure before cross-linking .
+.
+.
                    \begin{itemize}
                         \item Three different temperature systems have been set up and simulated for 20 ns (All with 20 layers and no vapor gap): 260K, 280K and 300K
+                          %MRS4: we will need longer than 20 ns to make sure they have stabilized.  We know there are structures that are at least metastable (our somewhat more disordered phase)
                         \item I have systems with no restraints on at all three temperatures
                         \item We can look at them with weak restraints in case the systems misbehave as time goes on. As of now, the tilt angles look to stabilize after 10 ns
-                        \item If we get stable configurations with correct XRD patterns at lower temps but not higher, it may be a consequence of the forcefield
+%MRS4: yea, the reason for weak restraints would be to kind of replace the force field errors -- i.e.
+what would it look like if it HAPPENED to have a slightly larger bias toward that configuration.
+Ideally, we won't need restraints.
+%MRS4: and maybe we do it with just the 3 temperatures first, before adding restraints.
+THere are so many variables, we want to be sure we are running simulations which are more likely to give results.
+                        \item If we get stable configurations with correct XRD patterns at lower temps but not higher, it may be a consequence of the forcefield %MRS: correct, though it's better if it works ok at 280 vs 260.
+We don't want it to start to crystallize.
                         \end{itemize}
@@
 		   \begin{itemize}
-                        \item Run out simulations with weak restraints (f = 0.1 kJ/mol*nm2)
+                        \item Run out simulations with weak restraints (f = 0.1 kJ/mol*nm2) %MRS4: or possibly weaker.
+Should work out the RMSD allowed by the restraints, and possibly let them move as much as 1/6 of the way around the circle.
                         \item Higher restraints may cause the system to be too ordered, but it may be worth running in the case of long term movement
@@
                    \begin{itemize}
+                     %MRS4: OK, so this is the same as above, except with no tilt in the monomers?
                         \item Offset, no vapor gap, 20 layer : No tilt (i.e.
@@
 The concern here is that I wont be able to get the monomers close enough together without causing some unreconcilable energy minimization errors.
+%MRS4: it is good to see if spots an appear from the tilt, though it looks like we can get them with layered configurations even w/o the tilt.
                         \item Offset, higher tilt.

### 2017-03-15 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Updating Methods
Switch from gap systems to no-gap systems with justification. Talk more about pi-stacking and how to set up the initial configuration. No mention of metastable states yet.

@@
 		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
+		\item Manual modifications to the structure were made to create specific geometries
 	\end{itemize}
@@
 
-	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
-        %MRS4: OK, but note that we will need to expand this to be enough convincing qualitative information.
+% 	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
+%         %MRS4: OK, but note that we will need to expand this to be enough convincing qualitative information.
 Could also use quantitaitve information about how far from the surface you see the effects of the surface.
-	\begin{itemize}
-		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
-		\item 5 layers create micellar structure
-		\item Beyond 20 layers is unnecessary to get expected configuration
-		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
-		\item How far into membrane do we have to go to avoid effects of the surface (this is a TODO)
-	\end{itemize}
+% 	\begin{itemize}
+% 		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
+% 		\item 5 layers create micellar structure
+% 		\item Beyond 20 layers is unnecessary to get expected configuration
+% 		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
+% 		\item How far into membrane do we have to go to avoid effects of the surface (this is a TODO)
+% 	\end{itemize}
 %MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
@@
 I can't think of a thesis for a figure that is purely illustrative
+	Each pore is made of twenty stacked monomer layers with continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport. 
+	\begin{itemize}
+		\item A thinner system is better to reduce the computational cost and allow us to look at longer timescales
+		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
 	FIGURE: initial configuration \\
@@
 	\begin{itemize}
-		\item SAXS gives an idea of Pore-to-Pore distances
+		\item XRD gives Pore-to-Pore distances of ~4.1 nm and indicates possible pi-stacking at ~3.7 Angstroms
+		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
+		\item T-shaped and parallel-displaced are nearly isoenergetic and more stable than the sandwiched configuration.
+		\item T-shaped configuration is most stable when benzene centers are ~ 5 A apart which is not consistent with WAXS. http://www.jbc.org/content/273/25/15458.full 
+		\item System made with stacked and parallel-displaced benzene rings to see what is favored and matches XRD
 		\item TEM images and rejection studies give a pore size estimate
@@
 			\item Leave position restraints for npt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
-			\item Gradually reduce force constants (by square root every 50 ps) until they are completely off
+			\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
 			\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate

### 2017-04-03 Ben_Manuscripts/XSEDE/bridges_2017/LLC_membranes.tex
Working on abstracts for ACS and AIChE and XSEDE proposal

subsection{How do water and ions move in nanostructured charged polymeric membranes?}
\subsubsection*{Background}

The ability to design nanostructured membranes with concomitant high chemical
specificity is an important goal of the membrane separations
community.~\cite{Humplik2011} The ability to control
the nanoscale architecture of membranes will allow membranes to be 
designed precisely for the purpose of separating specific compounds.
~\cite{SmithRC1997,Zhu2006} The membranes being studied in this project
have pores sizes smaller than 1 nanometer, allowing size-selective 
filtration of small molecules and gases, as well as desalination of salt
water based on charge repulsion and size-exclusion of hydrated salt ions.

%By studying the system with molecular detail, we will learning more
%about the mechanism of water and small solute transport through the
%membrane pores. These investigations will occur in close collaboration
%with experimentalists in the Gin and Noble group at the University of
%Colorado at Boulder who are working on the membranes at the lab
%scale.

The membrane system we propose to model in this project is composed of
lyotropic liquid crystals (LLCs) which self-assemble into hexagonally
packed, cylindrical pores with acidic groups facing toward the cylinder
center, complexed to counterions. Subsequent cross-linking to forms
a mechanically strong structure (Fig.~\ref{figure:membrane}).
~\cite{Zhou2003,Feng2014,Feng2016} The pores, at the level of resolution
obtained by SAXS and TEM, appear to be straight and uniform in size 
(Fig.~\ref{figure:membrane}).  This is very different from most 
commercially available membranes which have a pore size distribution
with tortuous pathways that reduce selectivity and flux respectively.
The ordered structure exhibited by LLC membranes makes them well suited 
for modeling using molecular dynamics simulations because the
system has a defined structure that can be studied in a reasonably sized 
unit cell.

Our initial systems were built by first parameterizing a single
monomer using the General Amber Force Field (GAFF). Because the
self-assembly process is long relative to times which we can simulate,
monomers were rotated into layers of six monomers and stacked into
cylinders to give a starting configuration close to where we expect
the system to settle at equilibrium. While a single lyotropic liquid
crystal consists of a small number of atoms (138), the entire unit
cell consists of about 66K atoms. This number increases to 
approximately 100K when water molecules are added to the system.

% BJC: The following is technically true although I've been creating
% specific configurations for testing purposes. 
In order to assemble the structures shown in Fig.~\ref{figure:membrane}, a
suitable monomer configuration needed to be chosen. Thermal annealing
of the monomer using GROMACS yielded many low energy configurations
close to what is expected.

Initial simulations have been performed which energy minimize and
allow the system to stabilize over the course of 20 ns in vacuum.  The
final structure and trajectory are analyzed quantitatively by
measuring pore size, distance between pores, and distribution of
sodium ions in the pore. These measurements are compared to values
measured experimentally with SAXS and TEM imaging in order to validate
the final structure. SAXS and TEM images were taken using dry membrane
which justifies our initial study of the system in vacuum.

\begin{figure}[h]
\begin{center}
\begin{tabular}{c}
\includegraphics[width=8cm]{modeled.png}\\
\includegraphics[height=5cm]{membrane2.pdf}\\
\end{tabular}
\end{center}
\caption{(above) SAXS and TEM experimental data, with hypothesized
  membrane structure. (Below, left) Top view of atomistic simulation,
  with hydrophilic head groups in orange, counterions in blue, and
  hydrophobic chains in blue. (Below, right) Side view of atomistic
  simulation showing counterions in dark blue and other atoms in light
  blue. These simulations demonstrate the heterogeneity in the
  modeled systems.~\label{figure:membrane}}
\end{figure}

\subsubsection*{Summary of Scientific Discoveries}

Our understanding of the microscopic structure of this type of LLC
membrane has greatly increased with the aid of simulations run using
Bridges.

Equilibration simulations of greater than 500 nanoseconds yield
stable membrane configurations with the expected HII phase 
morphology. Various methods have been developed to characterize
the equilibrated system. Generally, all equilibrium properties are
compared to experimental measurements. We validated two methods
for measuring ionic conductivity from atomistic simulations. Both 
methods require long simulations (at least 500 ns) in order to give
accurate statistics. The distance between pores is an important
structural parameter which we have measured using atomic coordinates
and by simulating X-ray diffraction (XRD) experiments, a relatively
undeveloped technique in MD for periodic systems such as ours. We 
have been able to generate structures which match experimental pore
spacings within reason.

The X-ray diffraction simulations also give detailed information
about membrane structure on the angstrom lengthscale. Our simulations
have produced two dimensional X-ray diffraction patterns that 
contain all major features present in experimental studies. Producing
a matching pattern was not trivial and resulted in the discovery of
two metastable states. The two states are defined by the degree of 
local order inside the pore regions. The state which we had initially
studied is characterized by a disordered pore region, however the X-ray
diffraction pattern does not match experiment. We altered the starting 
configuration so that the benzene rings in the head group of each
monomer were stacked in a parallel displaced configuration relative
to each other. The resulting X-ray diffraction pattern of the new
configuration, after equilibration, is a much closer match to experiment.
Additionally, we were able to explain the spots that appear (red arrows
in figure xx) contrary to how it was originally reported. The spots 
were assumed to be caused by the 40 degree tilt angle of the alkyl
tails with respect to the plane of each stacked monomer layer, a 
common feature of liquid crystal systems. However, we were able to 
produce the same spots using configurations with an average tilt angle
close to zero. Our most impactful finding remains as the discovery of 
two metastable states. This will be the subject of a publication which 
will be submitted in the coming months. In the future, we will conduct
free energy calculations that will help explain the difference between
the two states and and help predict what experimental conditions might
lead to each.

The next step for our system is to solvate it with water. In parallel 
to the preceding work, we have worked to develop methods which will be
used to study the solvated system. While measuring ionic conductivity 
and running XRD simulations will work just the same, equilibration is 
non-trivial. We do not know exactly the equilibrium content of water 
or where the water is situated. While it is clear that most water should be in the hydrophilic pore region, simulations have shown that an 
appreciable amount of water can exist in the tail region near the 
slightly hydrophilic ester group. The best way to figure out how much 
water should be in the pore is to run very long equilibration simulationsand allow the simulations to tell us. Our current approach is to create
water baths at each face of the membrane and allow water to diffuse into
the membrane. We have learned that we can equilibrate a membrane with
water in 1000 nanoseconds. Studies of the hydrated, 'lyotropic', phase
will be the subject of a subsequent publication.

\subsubsection*{Proposed Experiments and Justification of Resources}

% UPDATE
Vacuum simulations of this system with a unit cell consisting of 4
pores, each with twenty layers of six monomers, total 65K atoms. On
Bridges, using MPI-enabled GROMACS 5.1.2, we obtain
89 ns/day using 140 cores, beyond which the scaling becomes mildly
nonlinear (See Figure~\ref{figure:gromacs} in the ``Code Performance
and Scaling'' document for more details). Simulations of the same
system solvated in water results in a total of 104K atoms, which ran
at 86 ns/day using 224 cores, at the limit of the near linear scaling
regime.  By creating a system with 50 layers, we reached 210K atoms,
which scaled nearly linearly up to 64 ns/day on 336 cores. We will use
these timings to estimate the time required for these experiments.

%FREE ENERGY CALCULATIONS

%HIGH RESOLUTION XRD (to pick up additional features)

%CROSSLINKING?

Once equilibrated and cross-linked, we will examine the effect of
solvation of the membranes on the pores. We have learned that at least 
1000 ns of total simulation is required to observe full penetration of
water through pores resulting in a cost of 
%UPDATE
(2000 ns / (86 ns/day))\times~24
hours\times~224 cores = 124K required SU, if we assume the initial
membrane simulation boxes are sufficiently large.
%UPDATE

We will carry out the same procedure with a set of new monomers. In addition to the simulations outlined above, we will need to equilibrate each system
using the developed procedures. Equilibration for 500 ns

\begin{wraptable}{r}{0.4\textwidth} 
\begin{tabular}{|l|c|}
\hline
Simulation Set                & SU \\ 
\hline
Initial vacuum equilibration      &  57K \\
Test of monomer structuring       & 114K \\
System-size dependence            & 102K  \\
Membrane solvation                &  375K \\
Diffusion studies                 & 72K \\
Differences in bound counterion  & 430K \\
\hline
            Total         & 1140K \\
\hline
\end{tabular}

### 2017-04-05 Ben_Manuscripts/XSEDE/bridges_2017/progress.tex
XSEDE folder added

--- 2017-04-03 Ben_Manuscripts/XSEDE/bridges_2017/LLC_membranes.tex
@@
-subsection{How do water and ions move in nanostructured charged polymeric membranes?}
-\subsubsection*{Background}
+\section*{Summary of Scientific Discoveries}
 
-The ability to design nanostructured membranes with concomitant high chemical
-specificity is an important goal of the membrane separations
-community.~\cite{Humplik2011} The ability to control
-the nanoscale architecture of membranes will allow membranes to be 
-designed precisely for the purpose of separating specific compounds.
-~\cite{SmithRC1997,Zhu2006} The membranes being studied in this project
-have pores sizes smaller than 1 nanometer, allowing size-selective 
-filtration of small molecules and gases, as well as desalination of salt
-water based on charge repulsion and size-exclusion of hydrated salt ions.
-
-%By studying the system with molecular detail, we will learning more
-%about the mechanism of water and small solute transport through the
-%membrane pores. These investigations will occur in close collaboration
-%with experimentalists in the Gin and Noble group at the University of
-%Colorado at Boulder who are working on the membranes at the lab
-%scale.
-
-The membrane system we propose to model in this project is composed of
-lyotropic liquid crystals (LLCs) which self-assemble into hexagonally
-packed, cylindrical pores with acidic groups facing toward the cylinder
-center, complexed to counterions. Subsequent cross-linking to forms
-a mechanically strong structure (Fig.~\ref{figure:membrane}).
-~\cite{Zhou2003,Feng2014,Feng2016} The pores, at the level of resolution
-obtained by SAXS and TEM, appear to be straight and uniform in size 
-(Fig.~\ref{figure:membrane}).  This is very different from most 
-commercially available membranes which have a pore size distribution
-with tortuous pathways that reduce selectivity and flux respectively.
-The ordered structure exhibited by LLC membranes makes them well suited 
-for modeling using molecular dynamics simulations because the
-system has a defined structure that can be studied in a reasonably sized 
-unit cell.
-
-Our initial systems were built by first parameterizing a single
-monomer using the General Amber Force Field (GAFF). Because the
-self-assembly process is long relative to times which we can simulate,
-monomers were rotated into layers of six monomers and stacked into
-cylinders to give a starting configuration close to where we expect
-the system to settle at equilibrium. While a single lyotropic liquid
-crystal consists of a small number of atoms (138), the entire unit
-cell consists of about 66K atoms. This number increases to 
-approximately 100K when water molecules are added to the system.
-
-% BJC: The following is technically true although I've been creating
-% specific configurations for testing purposes. 
-In order to assemble the structures shown in Fig.~\ref{figure:membrane}, a
-suitable monomer configuration needed to be chosen. Thermal annealing
-of the monomer using GROMACS yielded many low energy configurations
-close to what is expected.
-
-Initial simulations have been performed which energy minimize and
-allow the system to stabilize over the course of 20 ns in vacuum.  The
-final structure and trajectory are analyzed quantitatively by
-measuring pore size, distance between pores, and distribution of
-sodium ions in the pore. These measurements are compared to values
-measured experimentally with SAXS and TEM imaging in order to validate
-the final structure. SAXS and TEM images were taken using dry membrane
-which justifies our initial study of the system in vacuum.
-
-\begin{figure}[h]
-\begin{center}
-\begin{tabular}{c}
-\includegraphics[width=8cm]{modeled.png}\\
-\includegraphics[height=5cm]{membrane2.pdf}\\
-\end{tabular}
-\end{center}
-\caption{(above) SAXS and TEM experimental data, with hypothesized
-  membrane structure. (Below, left) Top view of atomistic simulation,
-  with hydrophilic head groups in orange, counterions in blue, and
-  hydrophobic chains in blue. (Below, right) Side view of atomistic
-  simulation showing counterions in dark blue and other atoms in light
-  blue. These simulations demonstrate the heterogeneity in the
-  modeled systems.~\label{figure:membrane}}
-\end{figure}
-
-\subsubsection*{Summary of Scientific Discoveries}
-
+\subsection*{Simulations of transport in nanostructured polymer membranes}
 Our understanding of the microscopic structure of this type of LLC
@@
 
+\begin{figure}
+\caption{}
+\label{figure:metastable}
+\includegraphics[width=.9\textwidth]{porestructures.jpg}
+\centering
+\end{figure}
+
 The next step for our system is to solvate it with water. In parallel 
@@
 will be the subject of a subsequent publication.
-
-\subsubsection*{Proposed Experiments and Justification of Resources}
-
-% UPDATE
-Vacuum simulations of this system with a unit cell consisting of 4
-pores, each with twenty layers of six monomers, total 65K atoms. On
-Bridges, using MPI-enabled GROMACS 5.1.2, we obtain
-89 ns/day using 140 cores, beyond which the scaling becomes mildly
-nonlinear (See Figure~\ref{figure:gromacs} in the ``Code Performance
-and Scaling'' document for more details). Simulations of the same
-system solvated in water results in a total of 104K atoms, which ran
-at 86 ns/day using 224 cores, at the limit of the near linear scaling
-regime.  By creating a system with 50 layers, we reached 210K atoms,
-which scaled nearly linearly up to 64 ns/day on 336 cores. We will use
-these timings to estimate the time required for these experiments.
-
-%FREE ENERGY CALCULATIONS
-
-%HIGH RESOLUTION XRD (to pick up additional features)
-
-%CROSSLINKING?
-
-Once equilibrated and cross-linked, we will examine the effect of
-solvation of the membranes on the pores. We have learned that at least 
-1000 ns of total simulation is required to observe full penetration of
-water through pores resulting in a cost of 
-%UPDATE
-(2000 ns / (86 ns/day))\times~24
-hours\times~224 cores = 124K required SU, if we assume the initial
-membrane simulation boxes are sufficiently large.
-%UPDATE
-
-We will carry out the same procedure with a set of new monomers. In addition to the simulations outlined above, we will need to equilibrate each system
-using the developed procedures. Equilibration for 500 ns
-
-\begin{wraptable}{r}{0.4\textwidth} 
-\begin{tabular}{|l|c|}
-\hline
-Simulation Set                & SU \\ 
-\hline
-Initial vacuum equilibration      &  57K \\
-Test of monomer structuring       & 114K \\
-System-size dependence            & 102K  \\
-Membrane solvation                &  375K \\
-Diffusion studies                 & 72K \\
-Differences in bound counterion  & 430K \\
-\hline
-            Total         & 1140K \\
-\hline
-\end{tabular}

### 2017-04-05 Ben_Manuscripts/XSEDE/bridges_2017/proposed_work.tex
XSEDE folder added

--- 2017-04-03 Ben_Manuscripts/XSEDE/bridges_2017/LLC_membranes.tex
@@
 water based on charge repulsion and size-exclusion of hydrated salt ions.
-
-%By studying the system with molecular detail, we will learning more
-%about the mechanism of water and small solute transport through the
-%membrane pores. These investigations will occur in close collaboration
-%with experimentalists in the Gin and Noble group at the University of
-%Colorado at Boulder who are working on the membranes at the lab
-%scale.
 
@@
 
-\begin{figure}[h]
-\begin{center}
-\begin{tabular}{c}
-\includegraphics[width=8cm]{modeled.png}\\
-\includegraphics[height=5cm]{membrane2.pdf}\\
-\end{tabular}
-\end{center}
-\caption{(above) SAXS and TEM experimental data, with hypothesized
-  membrane structure. (Below, left) Top view of atomistic simulation,
-  with hydrophilic head groups in orange, counterions in blue, and
-  hydrophobic chains in blue. (Below, right) Side view of atomistic
-  simulation showing counterions in dark blue and other atoms in light
-  blue. These simulations demonstrate the heterogeneity in the
-  modeled systems.~\label{figure:membrane}}
-\end{figure}
-
-\subsubsection*{Summary of Scientific Discoveries}
-
-Our understanding of the microscopic structure of this type of LLC
-membrane has greatly increased with the aid of simulations run using
-Bridges.
-
-Equilibration simulations of greater than 500 nanoseconds yield
-stable membrane configurations with the expected HII phase 
-morphology. Various methods have been developed to characterize
-the equilibrated system. Generally, all equilibrium properties are
-compared to experimental measurements. We validated two methods
-for measuring ionic conductivity from atomistic simulations. Both 
-methods require long simulations (at least 500 ns) in order to give
-accurate statistics. The distance between pores is an important
-structural parameter which we have measured using atomic coordinates
-and by simulating X-ray diffraction (XRD) experiments, a relatively
-undeveloped technique in MD for periodic systems such as ours. We 
-have been able to generate structures which match experimental pore
-spacings within reason.
-
-The X-ray diffraction simulations also give detailed information
-about membrane structure on the angstrom lengthscale. Our simulations
-have produced two dimensional X-ray diffraction patterns that 
-contain all major features present in experimental studies. Producing
-a matching pattern was not trivial and resulted in the discovery of
-two metastable states. The two states are defined by the degree of 
-local order inside the pore regions. The state which we had initially
-studied is characterized by a disordered pore region, however the X-ray
-diffraction pattern does not match experiment. We altered the starting 
-configuration so that the benzene rings in the head group of each
-monomer were stacked in a parallel displaced configuration relative
-to each other. The resulting X-ray diffraction pattern of the new
-configuration, after equilibration, is a much closer match to experiment.
-Additionally, we were able to explain the spots that appear (red arrows
-in figure xx) contrary to how it was originally reported. The spots 
-were assumed to be caused by the 40 degree tilt angle of the alkyl
-tails with respect to the plane of each stacked monomer layer, a 
-common feature of liquid crystal systems. However, we were able to 
-produce the same spots using configurations with an average tilt angle
-close to zero. Our most impactful finding remains as the discovery of 
-two metastable states. This will be the subject of a publication which 
-will be submitted in the coming months. In the future, we will conduct
-free energy calculations that will help explain the difference between
-the two states and and help predict what experimental conditions might
-lead to each.
-
-The next step for our system is to solvate it with water. In parallel 
-to the preceding work, we have worked to develop methods which will be
-used to study the solvated system. While measuring ionic conductivity 
-and running XRD simulations will work just the same, equilibration is 
-non-trivial. We do not know exactly the equilibrium content of water 
-or where the water is situated. While it is clear that most water should be in the hydrophilic pore region, simulations have shown that an 
-appreciable amount of water can exist in the tail region near the 
-slightly hydrophilic ester group. The best way to figure out how much 
-water should be in the pore is to run very long equilibration simulationsand allow the simulations to tell us. Our current approach is to create
-water baths at each face of the membrane and allow water to diffuse into
-the membrane. We have learned that we can equilibrate a membrane with
-water in 1000 nanoseconds. Studies of the hydrated, 'lyotropic', phase
-will be the subject of a subsequent publication.
+%\begin{figure}[h]
+%\begin{center}
+%\begin{tabular}{c}
+%\includegraphics[width=8cm]{modeled.png}\\
+%\includegraphics[height=5cm]{membrane2.pdf}\\
+%\end{tabular}
+%\end{center}
+%\caption{(above) SAXS and TEM experimental data, with hypothesized
+%  membrane structure. (Below, left) Top view of atomistic simulation,
+%  with hydrophilic head groups in orange, counterions in blue, and
+%  hydrophobic chains in blue. (Below, right) Side view of atomistic
+%  simulation showing counterions in dark blue and other atoms in light
+%  blue. These simulations demonstrate the heterogeneity in the
+%  modeled systems.~\label{figure:membrane}}
+%\end{figure}
 
@@
 
-% UPDATE
 Vacuum simulations of this system with a unit cell consisting of 4
-pores, each with twenty layers of six monomers, total 65K atoms. On
+pores, each with twenty layers of six monomers, total 66K atoms. On
 Bridges, using MPI-enabled GROMACS 5.1.2, we obtain
-89 ns/day using 140 cores, beyond which the scaling becomes mildly
+99 ns/day using 224 cores, beyond which the scaling becomes mildly
 nonlinear (See Figure~\ref{figure:gromacs} in the ``Code Performance
 and Scaling'' document for more details). Simulations of the same
-system solvated in water results in a total of 104K atoms, which ran
-at 86 ns/day using 224 cores, at the limit of the near linear scaling
-regime.  By creating a system with 50 layers, we reached 210K atoms,
-which scaled nearly linearly up to 64 ns/day on 336 cores. We will use
+system solvated in water results in a total of 100K atoms, which ran
+at 121 ns/day using 336 cores, at the limit of the near linear scaling
+regime.  By creating a system with 80 layers, we reached 265K atoms,
+which scaled nearly linearly up to 29 ns/day on 224 cores. We will use
 these timings to estimate the time required for these experiments.
 
-%FREE ENERGY CALCULATIONS
+We repeated scaling studies with the same system using the GPU-enabled 
+GROMACS 2016 which was compiled for optimal use with NVIDIA Tesla K80
+accelerators. On Bridges we obtain 58 ns/day for the 66K atom system
+using 4 GPUs and 28 cores. Simulating the solvated configuration, we
+obtain 56.4 ns/day on 4 GPUs and 28 cores. Simulating the 265K atom 
+system we obtain 10.1 ns/day on 4 GPUs and 28 cores.
 
+In order to study the relative stability of the two metastable phases 
+we have discovered, we need will need to perform a computationally 
+intensive free energy calculation using the Multistate Bennett
+Acceptance Ratio (MBAR) technique. MBAR estimates free energy 
+difference with current lowest variance when compared to other estimators.
+In order to make a reasonable estimate, we will need to conduct 
+simulations all intermediate states which lead from one metastable
+state to another. Each configuration in the pathway mapping the two
+states must be sufficiently similar to adjacent configurations so that
+we achieve enough phase space overlap for a more precise calculation. 
+We estimate that we will need at least 50 intermediate states, each run
+for 50 ns for a total of 2500 ns of simulation time. This will require 
+(2500 ns / (99.2 ns/day))* 24 hrs/day * 224 cores = 135K SU using
+MPI on the RM partition. This will require (2500 ns / (58 ns/day)) * 24
+hours * 4 GPUs = 4.1K SU on the K80 GPU nodes.
+
+The resolution of simulated X-ray diffraction patterns is dependent on the
+size of the simulated unit cell. To create higher resolution patterns in 
+the x, y or z directions, requires an increase in the respective dimension
+of the unit cell by adding more atoms. The fundamental reason for this
+limitation is the necessity of meeting the Bragg condition. When met,
+constructive X-ray interference occurs, producing a signal on a nearby 
+detector. The lattice planes in the crystal, defined by the reciprocal
+space Miller indices h, k, and l, are separated by a distance, d. One can
+calculate all possible d values given all unit cell parameters. It is
+not trivial to see that an increase in box vector leads to a wider range
+of accessible hkl values and increases the resolution. A simple way to 
+estimate the simulated resolution in each direction is using the equations
+qx = 2*pi/x, qy = 2*pi/y, qz = 2*pi/z. Our current resolution with a 66K
+atom system is ~ 0.078 inverse angstroms. We propose a 4x increase in our
+z dimension resolution which will help us to distinguish reflections 
+deemed a consequence of benzene ring pi-stacking (reflection occurs at 1.53
+inverse angstroms) from simple alkane chain packing (reflection occurs
+between 1.4 and 1.57 inverse angstroms). We also hope to pick up finer 
+details such as the sharp line that appears at ~.85 inverse angstroms 
+experimentally but is absent in the simulated patterns. A system of this 
+type is made of 265K atoms. Stacking equilibrated membrane layers 
+directly on top of each will allow facilitate a fast equilibration of the
+large system. Equilibration will be allowed to run for at least 50 ns 
+followed by 50 ns of simulation needed to collect enough information to
+simulate the XRD pattern. 100 ns of simulation time for a 265K atom system 
+will require 19K SU on the RM nodes and 950 SU on K80 GPU nodes.     
 %HIGH RESOLUTION XRD (to pick up additional features)
@@
 %UPDATE
-(2000 ns / (86 ns/day))\times~24
-hours\times~224 cores = 124K required SU, if we assume the initial
+(2000 ns / (86 ns/day)) * 24
+hours * 224 cores = 124K required SU, if we assume the initial
 membrane simulation boxes are sufficiently large.
@@
 
-\begin{wraptable}{r}{0.4\textwidth} 
-\begin{tabular}{|l|c|}
-\hline
-Simulation Set                & SU \\ 
-\hline
-Initial vacuum equilibration      &  57K \\
-Test of monomer structuring       & 114K \\
-System-size dependence            & 102K  \\
-Membrane solvation                &  375K \\
-Diffusion studies                 & 72K \\
-Differences in bound counterion  & 430K \\
-\hline
-            Total         & 1140K \\
-\hline
-\end{tabular}
+%\begin{wraptable}{r}{0.4\textwidth} 
+%\begin{tabular}{|l|c|}
+%\hline
+%Simulation Set                & SU \\ 
+%\hline
+%Initial vacuum equilibration      &  57K \\
+%Test of monomer structuring       & 114K \\
+%System-size dependence            & 102K  \\
+%Membrane solvation                &  375K \\
+%Diffusion studies                 & 72K \\
+%Differences in bound counterion  & 430K \\
+%\hline
+%            Total         & 1140K \\
+%\hline
+%\end{tabular}

### 2017-04-06 Ben_Manuscripts/XSEDE/bridges_2017/proposed_work.tex
updated XSEDE

@@
 
-We repeated scaling studies with the same system using the GPU-enabled 
+We repeated scaling studies with the same system using GPU-enabled 
 GROMACS 2016 which was compiled for optimal use with NVIDIA Tesla K80
-accelerators. On Bridges we obtain 58 ns/day for the 66K atom system
-using 4 GPUs and 28 cores. Simulating the solvated configuration, we
-obtain 56.4 ns/day on 4 GPUs and 28 cores. Simulating the 265K atom 
-system we obtain 10.1 ns/day on 4 GPUs and 28 cores.
+accelerators. On Bridges we obtain 58 ns/day, 56.4 ns/day and 10.1 ns/day
+for the 66K, 100K and 256K atom systems respectively. Although the system
+scales nearly linearly for greater than 4 GPUs in all cases, additional
+GPUs require more than 1 node which has signficantly extended queue wait
+times in our experience. It is preferable to run jobs longer on one GPU
+for a long time than to delay a job from starting but have it run for a
+shorter time. Since trajectory files are written while simulating, it
+is beneficial to check progress and cancel jobs which show no value.
+We plan to work with PSC to compile a version of gromacs that is performs
+optimally with the
 

### 2017-04-06 Ben_Manuscripts/XSEDE/bridges_2017/proposed_work.tex
Most of the content is there

@@
-subsection{How do water and ions move in nanostructured charged polymeric membranes?}
+\subsection{How do water and ions move in nanostructured charged polymeric membranes?}
 \subsubsection*{Background}
@@
 packed, cylindrical pores with acidic groups facing toward the cylinder
-center, complexed to counterions. Subsequent cross-linking to forms
-a mechanically strong structure (Fig.~\ref{figure:membrane}).
-~\cite{Zhou2003,Feng2014,Feng2016} The pores, at the level of resolution
-obtained by SAXS and TEM, appear to be straight and uniform in size 
-(Fig.~\ref{figure:membrane}).  This is very different from most 
-commercially available membranes which have a pore size distribution
-with tortuous pathways that reduce selectivity and flux respectively.
-The ordered structure exhibited by LLC membranes makes them well suited 
-for modeling using molecular dynamics simulations because the
-system has a defined structure that can be studied in a reasonably sized 
-unit cell.
+center, complexed to counterions. Subsequent cross-linking of vinyl
+groups on monomer tail ends forms a mechanically strong structure
+(Fig.~\ref{figure:membrane}). ~\cite{Zhou2003,Feng2014,Feng2016}
+The pores, at the level of resolution obtained by SAXS and TEM, appear
+to be straight and uniform in size (Fig.~\ref{figure:membrane}). 
+This is very different from most commercially available membranes 
+which have a pore size distribution with tortuous pathways that reduce
+selectivity and flux respectively. The ordered structure exhibited by
+LLC membranes makes them well suited for modeling using molecular 
+dynamics simulations because the system has a defined structure that
+can be studied in detail with a reasonably sized unit cell.
 
@@
 
-% BJC: The following is technically true although I've been creating
-% specific configurations for testing purposes. 
-In order to assemble the structures shown in Fig.~\ref{figure:membrane}, a
-suitable monomer configuration needed to be chosen. Thermal annealing
-of the monomer using GROMACS yielded many low energy configurations
-close to what is expected.
-
-Initial simulations have been performed which energy minimize and
-allow the system to stabilize over the course of 20 ns in vacuum.  The
+Equilibration simulations have been performed which energy minimize and
+allow the system to stabilize over the course of 500 ns in vacuum.  The
 final structure and trajectory are analyzed quantitatively by
-measuring pore size, distance between pores, and distribution of
-sodium ions in the pore. These measurements are compared to values
+measuring pore size, distance between pores, distribution of
+sodium ions in the pore, simulating X-ray diffraction patterns and 
+calculating ionic conductivity. These measurements are compared to values
 measured experimentally with SAXS and TEM imaging in order to validate
@@
 
-%\begin{figure}[h]
-%\begin{center}
-%\begin{tabular}{c}
-%\includegraphics[width=8cm]{modeled.png}\\
-%\includegraphics[height=5cm]{membrane2.pdf}\\
-%\end{tabular}
-%\end{center}
-%\caption{(above) SAXS and TEM experimental data, with hypothesized
-%  membrane structure. (Below, left) Top view of atomistic simulation,
-%  with hydrophilic head groups in orange, counterions in blue, and
-%  hydrophobic chains in blue. (Below, right) Side view of atomistic
-%  simulation showing counterions in dark blue and other atoms in light
-%  blue. These simulations demonstrate the heterogeneity in the
-%  modeled systems.~\label{figure:membrane}}
-%\end{figure}
+\begin{figure}[h]
+\begin{center}
+\begin{tabular}{c}
+\includegraphics[width=8cm]{modeled.png}\\
+\includegraphics[height=5cm]{membraneviews.png}\\
+\end{tabular}
+\end{center}
+\caption{(above) SAXS and TEM experimental data, with hypothesized
+  membrane structure. (Below, left) Top view of atomistic simulation,
+  with hydrophilic head groups in orange, counterions in blue, and
+  hydrophobic chains in blue. (Below, right) Side view of atomistic
+  simulation showing counterions in dark blue and other atoms in light
+  blue. These simulations demonstrate the heterogeneity in the
+  modeled systems.~\label{figure:membrane}}
+\end{figure}
 
@@
 
-We repeated scaling studies with the same system using GPU-enabled 
-GROMACS 2016 which was compiled for optimal use with NVIDIA Tesla K80
-accelerators. On Bridges we obtain 58 ns/day, 56.4 ns/day and 10.1 ns/day
+We repeated scaling studies with the same systems using GPU-enabled 
+GROMACS 2016 with both the NVIDIA K80 and NVIDIA P100 GPUs available on
+Bridges. Using 4 K80 GPUs we obtain 58 ns/day, 56.4 ns/day and 10.1 ns/day
 for the 66K, 100K and 256K atom systems respectively. Although the system
@@
 In order to study the relative stability of the two metastable phases 
-we have discovered, we need will need to perform a computationally 
+we have discovered, we will need to perform a computationally 
 intensive free energy calculation using the Multistate Bennett
 Acceptance Ratio (MBAR) technique. MBAR estimates free energy 
-difference with current lowest variance when compared to other estimators.
-In order to make a reasonable estimate, we will need to conduct 
-simulations all intermediate states which lead from one metastable
+differences with the currently lowest variance when compared to other
+estimators. In order to make a reasonable estimate, we will need to 
+conduct simulations of all intermediate states which lead from one metastable
 state to another. Each configuration in the pathway mapping the two
@@
 limitation is the necessity of meeting the Bragg condition. When met,
-constructive X-ray interference occurs, producing a signal on a nearby 
-detector. The lattice planes in the crystal, defined by the reciprocal
-space Miller indices h, k, and l, are separated by a distance, d. One can
-calculate all possible d values given all unit cell parameters. It is
-not trivial to see that an increase in box vector leads to a wider range
-of accessible hkl values and increases the resolution. A simple way to 
-estimate the simulated resolution in each direction is using the equations
-qx = 2*pi/x, qy = 2*pi/y, qz = 2*pi/z. Our current resolution with a 66K
-atom system is ~ 0.078 inverse angstroms. We propose a 4x increase in our
-z dimension resolution which will help us to distinguish reflections 
-deemed a consequence of benzene ring pi-stacking (reflection occurs at 1.53
-inverse angstroms) from simple alkane chain packing (reflection occurs
-between 1.4 and 1.57 inverse angstroms). We also hope to pick up finer 
-details such as the sharp line that appears at ~.85 inverse angstroms 
-experimentally but is absent in the simulated patterns. A system of this 
-type is made of 265K atoms. Stacking equilibrated membrane layers 
-directly on top of each will allow facilitate a fast equilibration of the
-large system. Equilibration will be allowed to run for at least 50 ns 
-followed by 50 ns of simulation needed to collect enough information to
-simulate the XRD pattern. 100 ns of simulation time for a 265K atom system 
-will require 19K SU on the RM nodes and 950 SU on K80 GPU nodes.     
-%HIGH RESOLUTION XRD (to pick up additional features)
+constructive X-ray interference occurs resulting in a signal which gives
+details about the position of atoms relative to each other. The lattice
+planes in the crystal, defined by the reciprocal space Miller indices 
+h, k, and l, are separated by a distance, d. One can calculate all possible
+d values given all unit cell parameters. It is not trivial to see that an
+increase in box vector leads to a wider range of accessible hkl values 
+and increases the spatial resolution. A simple way to estimate the simulated
+resolution in each direction is using the equations qx = 2*pi/x, qy = 2*pi/y,
+qz = 2*pi/z. Our current resolution with a 66K atom system is ~ 0.078 inverse
+angstroms (Fig.~\ref{fig:expxrdcomp}). We propose a 4x increase in our z dimension resolution which will
+help us to distinguish reflections deemed a consequence of benzene ring 
+pi-stacking (reflection occurs at 1.53 inverse angstroms) from simple
+alkane chain packing (reflection occurs between 1.4 and 1.57 inverse
+angstroms). We also hope to pick up finer details such as the sharp line
+that appears at ~.85 inverse angstroms experimentally but is absent in 
+the simulated patterns. A system of this size is made of 265K atoms. 
+Stacking equilibrated membrane layers directly on top of each will 
+facilitate a fast equilibration of the large system. Equilibration 
+simulations will be run for at least 50 ns followed by another 50 ns of 
+simulation needed to collect enough information to simulate the XRD 
+pattern. 100 ns of simulation time for a 265K atom system will require 
+19K SU on the RM nodes and 950 SU on K80 GPU nodes.
 
-%CROSSLINKING?
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{Sim_exp_xrd_sidebyside.png}
+	\caption{(left) Experimental Wide Angle X-ray Diffraction experiments contain
+reflections at qz \approx 1.7 A $^{-1}$ indicating pi-stacking of benzene
+rings in the monomer head group. A weak, correlated reflection is present at 
+qz \approx 0.85 A $^{-1}$. (right) Simulated X-ray diffraction shows a pi-stacking reflection
+at qz \approx 1.5 A $^{-1}$. The weak correlated reflection is not
+present but may be visible with higher resolution simulations}
+	\label{fig:expxrdcomp}
 
-Once equilibrated and cross-linked, we will examine the effect of
-solvation of the membranes on the pores. We have learned that at least 
-1000 ns of total simulation is required to observe full penetration of
-water through pores resulting in a cost of 
-%UPDATE
-(2000 ns / (86 ns/day)) * 24
-hours * 224 cores = 124K required SU, if we assume the initial
+\end{figure}
+
+Once equilibrated and cross-linked, we will examine the effect of membrane
+solvation on the pore structure and corresponding transport properties.
+We have learned that at least 1000 ns of total simulation is required
+to fully equilibrate the system with water. (1000 ns / (86 ns/day)) * 24
+hours * 224 cores = 62K required SU, if we assume the initial
 membrane simulation boxes are sufficiently large.
-%UPDATE
 
-We will carry out the same procedure with a set of new monomers. In addition to the simulations outlined above, we will need to equilibrate each system
-using the developed procedures. Equilibration for 500 ns
+We will carry out the same procedure with a new set of monomers similar
+in structure to the current monomer. Simple modifications can be made
+to the monomer structure as outlined in Figure ~\ref{fig:chemistries}. 
+We will need to equilibrate each system using developed procedures which
+requires equilibration simulations of at least 500 ns. Of the 
+possibilities outlined in Figure ~\ref{fig:chemistries} we will try all
+variations of tail spacer and ionic headgroup and at least 3 counterions
+of different charge (+1, +2, +3). This results in a total of 24 systems 
+that require 500 ns of equilbration time. These length simulations should
+also give us the required information to calculate physical properties 
+such as ionic conductivity, and to simulate X-ray diffraction patterns.
+We will require xxx SU explore this space. To solvate all the test
+systems, an additional xxx SU will be necessary.
+
+We will conduct transport studies on all systems in order to relate pore
+structure to macroscopic observables such as water flux and solute
+rejection. We will measure diffusion of various solutes across the 
+membrane. Understanding the mechanims of transport of each solute will
+provide us with sufficient understanding to suggest new modifications 
+to monomer structure that should increase laboratory performance. We
+anticipate simulations of at least 50 ns will be necessary to get 
+sufficient sampling for an informative mean square displacement (MSD) 
+curve. The MSD curve will make it easier to identify potential 
+transport mechanisms based on its shape.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{chemistries.png}  % who made this picture? It has a typo : "ionic headgoup"
+	\caption{LLC chemistries we will examine in order to understand determinants of pore size, structure and solute transport}
+	\label{fig:chemistries}
+\end{figure}
 

### 2017-04-10 Ben_Manuscripts/Outlines/Paper1_Outline.tex
updates

--- 2017-03-15 Ben_Manuscripts/Paper1/Paper1_Outline.tex
@@
 	\section{Introduction}
-	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale.
+	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale allowing design of solute-specific separation membranes.
 	\begin{itemize}
@@
 		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
-		\item Entirely different mechanisms govern the separation processes in various nano structured materials which can inspire novel separation techniques
+		\item Entirely different mechanisms govern the separation processes in various nanostructured materials which can inspire novel separation techniques
 	\end{itemize}
@@
 		\begin{itemize}
-			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact 
+			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact selectivity
 			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
@@
 
-	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines for design of monomers used to create separation-specific membranes.
+	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines to reduce the chemical space for design of monomers used to create separation-specific membranes.
 	\begin{itemize}
-		\item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effect water desalination and small organic separations.
-Rejection studies show that this membrane can't do desalination
-		\item We can create a molecular model that will give us the desired understanding
-		\item Our focus is on Colh since it is a simpler system and has the same experimental data
-		\item Colh phase studies currently limited mostly to one monomer
-		\item Optimization efforts performed through trial and error
+                \item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effective water desalination and small organic separations.
+Rejection studies show that this membrane can not do desalination yet
+		\item Colh phase studies currently limited to one monomer
+                \item Optimization efforts performed through trial and error over the past 20 years
                 \item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
-		\item An atomistic understanding of the mechanism of solute transport can identify
-		performance bottle necks and direct design of future monomers/membranes
                 \begin{itemize}
@@
                         \item Is water structured inside the pores leading to transport barriers?
-		\end{itemize}
+			\item What does the microscopic pore structure look like and how can we relate that to monomer design and transport?
+		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
+		\item We can use molecular dynamics simulations to enhance our understanding 
 	\end{itemize}
@@
 		\end{itemize}
+		\item How do the monomer head groups prefer to be oriented relative to each other?
+		\begin{itemize}		
 			\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
+			\begin{itemize}
+				\item Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
+				\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation.
+%BJC: Although the system is made of bulky substituted benzenes, I think it's easy to see how one can hypothesize for our system based on the simpler system.
 		\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk

### 2017-04-10 Ben_Manuscripts/XSEDE/bridges_2017/proposed_work.tex

@@
 measured experimentally with SAXS and TEM imaging in order to validate
-the final structure. SAXS and TEM images were taken using dry membrane
+the final structure. SAXS and TEM images were taken using dry membranes
 which justifies our initial study of the system in vacuum.
@@
 99 ns/day using 224 cores, beyond which the scaling becomes mildly
-nonlinear (See Figure~\ref{figure:gromacs} in the ``Code Performance
+nonlinear (See Figure~\ref{figure:LLCscaling} in the ``Code Performance
 and Scaling'' document for more details). Simulations of the same
 system solvated in water results in a total of 100K atoms, which ran
-at 121 ns/day using 336 cores, at the limit of the near linear scaling
+at 84.2 ns/day using 224 cores, at the limit of the near linear scaling
 regime.  By creating a system with 80 layers, we reached 265K atoms,
@@
 Bridges. Using 4 K80 GPUs we obtain 58 ns/day, 56.4 ns/day and 10.1 ns/day
-for the 66K, 100K and 256K atom systems respectively. Although the system
-scales nearly linearly for greater than 4 GPUs in all cases, additional
-GPUs require more than 1 node which has signficantly extended queue wait
-times in our experience. It is preferable to run jobs longer on one GPU
-for a long time than to delay a job from starting but have it run for a
-shorter time. Since trajectory files are written while simulating, it
-is beneficial to check progress and cancel jobs which show no value.
-We plan to work with PSC to compile a version of gromacs that is performs
-optimally with the
+for the 66K, 100K and 256K atom systems respectively. Using 4 P100 GPUs, 
+we obtain 83.6 ns/day, 62.0 ns/day and 18.8 ns/day for each system 
+respectively. Although in some cases, the system scales nearly linearly
+for greater than 4 GPUs, additional GPUs signficantly extends queue wait
+times due to high demand. The cost will be the same, but starting simulations
+earlier will allow analysis to be performed during simulations and prevent
+valueless simulation from preceding, saving computer time.
 
-In order to study the relative stability of the two metastable phases 
+In order to study the relative stability of the two metastable states
 we have discovered, we will need to perform a computationally 
@@
 (2500 ns / (99.2 ns/day))* 24 hrs/day * 224 cores = 135K SU using
-MPI on the RM partition. This will require (2500 ns / (58 ns/day)) * 24
-hours * 4 GPUs = 4.1K SU on the K80 GPU nodes.
+MPI on the RM partition, (2500 ns / (58 ns/day)) * 24 hours * 4 GPUs * 1 SU
+/ GPU-hour = 4.1K SU on the K80 GPU nodes, and (2500 ns / (83.6 ns/day)) 
+* 24 hours * 4 GPUs * 2.5 SU / GPU-hour = 7.2K SU on the P100 GPU nodes.
 
@@
 and increases the spatial resolution. A simple way to estimate the simulated
-resolution in each direction is using the equations qx = 2*pi/x, qy = 2*pi/y,
-qz = 2*pi/z. Our current resolution with a 66K atom system is ~ 0.078 inverse
-angstroms (Fig.~\ref{fig:expxrdcomp}). We propose a 4x increase in our z dimension resolution which will
+resolution in each direction is using the equations qx = 2$\pi$/Lx, qy =
+2$\pi$/Ly, qz = 2$\pi$/Lz. Our current resolution with a 66K atom system is ~ 0.078 $A^{-1}$ (Fig.~\ref{fig:expxrdcomp}). 
+We propose a 4x increase in our z dimension resolution which will
 help us to distinguish reflections deemed a consequence of benzene ring 
@@
 pattern. 100 ns of simulation time for a 265K atom system will require 
-19K SU on the RM nodes and 950 SU on K80 GPU nodes.
-
+19K SU on the RM nodes, 950 SU on K80 GPU nodes, and 1.3K SU on P100 GPU nodes.     
 \begin{figure}
@@
 
-Once equilibrated and cross-linked, we will examine the effect of membrane
+Once equilibrated and cross-linked (an algorithm which can run without the 
+aid of an HPC resource), we will examine the effect of membrane
 solvation on the pore structure and corresponding transport properties.
 We have learned that at least 1000 ns of total simulation is required
-to fully equilibrate the system with water. (1000 ns / (86 ns/day)) * 24
-hours * 224 cores = 62K required SU, if we assume the initial
-membrane simulation boxes are sufficiently large.
+to fully equilibrate the system with water. These simulations will require
+(1000 ns / (84.2 ns/day)) * 24 hours * 224 cores = 64K SU on RM nodes, 
+(1000 ns / (56.4 ns/day)) * 24 hours * 4 GPUs * 1 SU / GPU-hour = 1.7K SU on K80 GPU nodes and
+(1000 ns / (62 ns/day)) * 24 hours * 4 GPUs * 2.5 SU / GPU-hour = 3.9 SU on P100 GPU nodes.
 
@@
 variations of tail spacer and ionic headgroup and at least 3 counterions
-of different charge (+1, +2, +3). This results in a total of 24 systems 
+of different charge (+1, +2, +3). This results in a total of 23 new systems 
 that require 500 ns of equilbration time. These length simulations should
@@
 such as ionic conductivity, and to simulate X-ray diffraction patterns.
-We will require xxx SU explore this space. To solvate all the test
-systems, an additional xxx SU will be necessary.
+To run these simulations, a total of 12000 ns, we will require 623K, 19K, 
+or 34K SU on the RM, K80 or P100 nodes respectively. To solvate all the test
+systems, an additional 1250K, 38K, or 68K SU will be required for the RM
+K80 or P100 nodes respectively.
+% BJC: obviously this is a lot. We should talk more about this to narrow 
+% the space. Although, we can always just ask for it and see what happens.
 
@@
 sufficient sampling for an informative mean square displacement (MSD) 
-curve. The MSD curve will make it easier to identify potential 
-transport mechanisms based on its shape.
+curve. Based on the shape of the MSD curve we can identify potential 
+transport mechanisms. Based on quantitative studies of the structure
+of the 24 equilibrated systems already studied, we will narrow our 
+design space to 5 with the most potential. We will study transport in % 5 is pretty arbitrary here
+each of the five with at least 5 solutes of varying charge and 
+hydrodynamic radii. This will require a total of 25 50 ns simulations for
+a total of 1250 ns of solvated system simulation. This will require
+80K, 2.1K or 4.8K SU using RM, K80 or P100 nodes respectively.
 
@@
 %\hline
-%Simulation Set                & SU \\ 
+%Simulation Set               & RM SU & K80 SU & P100 SU \\ 
 %\hline
-%Initial vacuum equilibration      &  57K \\
-%Test of monomer structuring       & 114K \\
-%System-size dependence            & 102K  \\
-%Membrane solvation                &  375K \\
-%Diffusion studies                 & 72K \\
-%Differences in bound counterion  & 430K \\
+%Free Energy Calculation      & 135K  & 4.1K   & 7.2K    \\
+%High Resolution XRD          & 19K   & 950    & 1.3K    \\
+%Vacuum Equilibration         & 650K  & 19K    & 34K     \\
+%Membrane Solvation           & 1250K & 38K    & 68K     \\
+%Transport studies            & 80K   & 2.1K   & 4.8K    \\
 %\hline
-%            Total         & 1140K \\
+%            Total            & 2134K & 64.15K & 115.3K \\
 %\hline

### 2017-04-10 Ben_Manuscripts/Outlines/Paper1_Outline.tex

@@
 	\bibliographystyle{ieeetr}
+	\graphicspath{{./figures/}}
 	\maketitle
@@
 		\end{itemize}
-		\item How do the monomer head groups prefer to be oriented relative to each other?
-		\begin{itemize}		
 		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
 		\begin{itemize}
-				\item Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
+			\item How do the monomer head groups pack together? Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
 			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation.
@@
 			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
-		\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each 
+			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer 
 			\item We can use fourier analysis to determine if there are distinct layers, and if so, how many monomers are situated in each layer.
+		\end{itemize}
+		\item It is possible there are more than one metastable states associated with this LLC system
+		\begin{itemize}
+			\item Which phase is consistent with experiment?
+			\item Can both phases be created experimentally?
+			\item How will each state affect transport?
+		\end{itemize}
 	\end{itemize}
@@
 		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
-		\item We are primarily interested in reproducing the conclusions about structure which can be made from SAXS experiments, predicting ionic conductivity with a reasonable comparison to experiment, and reproducing experimental density measurements.
-			\item We can simulate x ray diffraction patterns based on atomic coordinates
+		\item We are primarily interested in reproducing the conclusions about structure which have been made from SAXS experiments and ionic conductivity  measurements.    
+		\item We have written an algorithm to simulate the crosslinking mechanism and understand its influence on membrane structure
+		\item We can simulate x ray diffraction patterns based on atomic coordinates in order to compare major feature present in the 2D patterns
 		\item We can predict ionic conductivity using two agreeing methods
-			\item Density? - I will ask Mike to take more density measurements. It seems worthwhile     
 	\end{itemize}
@@
 I can't think of a thesis for a figure that is purely illustrative
-	Each pore is made of twenty stacked monomer layers with continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport. 
+	Each pore is made of twenty stacked monomer layers with continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
 	\begin{itemize}
@@
 		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
-	FIGURE: initial configuration \\
-	caption: A representative initial configuration. Each pore is rotated about the z axis rotated to prevent overlaps between pores \\
-	\\
+
+	\begin{figure}
+	\includegraphics{placeholder.tex}
+		\caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
+		\label{fig:initial}
+	\end{figure}
+
 	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
 	\begin{itemize}
-		\item XRD gives Pore-to-Pore distances of ~4.1 nm and indicates possible pi-stacking at ~3.7 Angstroms
+		\item XRD gives Pore-to-Pore distances of ~4.1 nm and indicates possible pi-stacking at ~3.7 Angstroms (see figure blah blah later on - comparison of experimental vs. simulated)
 		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
@@
 		\item TEM images and rejection studies give a pore size estimate
-		\item To prevent unrealistic jumps during initial equilibration steps, the following equilibration scheme was adopted
+
+	To prevent unrealistic jumps caused by poor atom placement during early equilibration steps, the following equilibration scheme was adopted.
 		\begin{itemize}
@@
 
-	Appropriate selection of initial structural parameters including interlayer spacing, relative interlayer orientation, and pore spacing results in an equilibrated model that is experimentally consistent.
+	Simulations of systems built by stacking monomers in the parallel-displaced and stacked configurations results in two different structures that are both stable for $>$ 500 ns, suggesting the existence of more than one metastable state.
 	\begin{itemize}
-		\item Visual perspective \\
-%MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
-		FIGURE: shows top view and cross section (with pbcs on)\\
-		caption: \\ 
-		(a) The expected hexagonal membrane morphology is preserved upon equilibration \\
-		(b) Straight cylindrical pore regions are present \\
-		\item System dimensions and properties are consistent upon equilibration using multiple monomer configurations 
-		\item Pore to pore distance
-		\begin{itemize}
-			\item We know from SAXS data what the distance between pores should be
-			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
-			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
+		\item There are distinct differences in the pore structures between each state (Fig ~\ref{fig:porestructures})
+		\item The stacked configuration results in a pore with high radial disorder. 
+		\item The parallel displaced configuration results in an open cylindrical pore.
+Benzene rings remain offset and form a helix.
+The membrane is thinner and the pore spacing is greater.
+Density stays the same (?)
 	\end{itemize}
 
-		FIGURE - 2 panels \\
-		(a) Measuring the distance between pores over time indicates equilibration when the distances stop changing \\
-		(b) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\
+	\begin{figure}
+	\centering
+	\includegraphics{placeholder.pdf}
+		\caption{Different pore structure are clear between systems built with benzene rings layered in a (a) stacked or (b) parallel-displaced conformation}
+		\label{fig:porestructures}
+	\end{figure}
 
-		\item Simulated X-ray Diffraction
+	Comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration
 	\begin{itemize} 
-			\item We used the 3 dimensional fourier transformed electron density to generate simulated 1D and 2D diffraction patterns
-			\item The 1D patterns are generated by spherical integration of the FT
-			\item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
-			\item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
-		\end{itemize}
+		\item Stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock
+		\item Those reflections are present from the 2D 
+%	Appropriate selection of initial structural parameters including interlayer spacing, relative interlayer orientation, and pore spacing results in an equilibrated model that is experimentally consistent.
+%	\begin{itemize}
+%		\item Visual perspective \\
+%MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
+%		FIGURE: shows top view and cross section (with pbcs on)\\
+%		caption: \\ 
+%		(a) The expected hexagonal membrane morphology is preserved upon equilibration \\
+%		(b) Straight cylindrical pore regions are present \\
+%		\item System dimensions and properties are consistent upon equilibration using multiple monomer configurations 
+%		\item Pore to pore distance
+%		\begin{itemize}
+%			\item We know from SAXS data what the distance between pores should be
+%			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
+%			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
+%		\end{itemize}
 
+%		FIGURE - 2 panels \\
+%		(a) Measuring the distance between pores over time indicates equilibration when the distances stop changing \\
+%		(b) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\
+
+%		\item Simulated X-ray Diffraction
+%		\begin{itemize}
+%			\item We used the 3 dimensional fourier transformed electron density to generate simulated 1D and 2D diffraction patterns
+%			\item The 1D patterns are generated by spherical integration of the FT
+%			\item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
+%			\item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
+%		\end{itemize}
+%	        
 		FIGURE - 4 panels \\

### 2017-04-20 Ben_Manuscripts/Outlines/Paper1_Outline.tex
updating outline

@@
 		\item Synthetic techniques are cheap and amenable to creating any monomer in this large design space
-		\item LLCs forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
-		\item Na-GA3C11 forms two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII)
-		%BJC: this is making me scratch my head - I'm afraid to talk a lot about this because of Mike's new data. But I think it's important to distinguish between what has been reported in past literature 
+		\item LLCs forms lamellar, bicontinuous cubic and hexagonal phases based on solution composition
+		\item Na-GA3C11 has been described in literature as forming two types of self assembled phases - thermotropic (Colh) and lyotropic (HII)
 		\item The thermotropic, Colh, is formed by the self assembly of neat monomer
 		\item The lyotropic, HII phase is formed in the presence of small amounts of water
-		\item Both assemble into cylinders with hydrophilic groups oriented inward towards the pore center and hydrophobic group facing outward.
+		\item Both assemble into cylinders with hydrophilic groups oriented inward towards the pore center and hydrophobic groups facing outward.
 The only difference is the inclusion of water in the structure which leads to minor variations in the structure with potentially different filtration properties (although no filtration experiments have been done on Colh)
@@
 		\item Until recently, they could not be aligned - hindered progress
-		\item Yale aligns them, then crosslinks them to lock in the structure - reference 2014 and 2016 papers
+		\item Yale aligns them, then crosslinks them to lock in the structure - reference 2014 and 2016 papers. They say that they are scalable techniques
 		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
@@
 
-	A clear picture of the microscopic structure of LLC membranes, gained by building a molecular model, will confirm or deny past drawn conclusions that have largely guided our understanding of separation mechanisms.
+	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, will confirm or deny past drawn conclusions that have largely guided our understanding of separation mechanisms.
 	\begin{itemize}
@@
 			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
-%BJC: Although the system is made of bulky substituted benzenes, I think it's easy to see how one can hypothesize for our system based on the simpler system.
+			\item Substituted benzene preferred stacking mode? Learning more about this   	
 			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
 			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer 
-			\item We can use fourier analysis to determine if there are distinct layers, and if so, how many monomers are situated in each layer.
+			\item Does the equilibrated structure exist in distinct layers? Fourier analysis can help answer this question
 		\end{itemize}
-		\item It is possible there are more than one metastable states associated with this LLC system
+		\item It is possible there is more than one metastable states associated with this LLC system
 		\begin{itemize}
@@
 		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
-		\item We are primarily interested in reproducing the conclusions about structure which have been made from SAXS experiments and ionic conductivity  measurements.    
+		\item We are primarily interested in reproducing the conclusions about structure which have been made from XRD experiments and ionic conductivity measurements.    
 		\item We have written an algorithm to simulate the crosslinking mechanism and understand its influence on membrane structure
-		\item We can simulate x ray diffraction patterns based on atomic coordinates in order to compare major feature present in the 2D patterns
-		\item We can predict ionic conductivity using two agreeing methods
+		\item We can simulate x ray diffraction patterns based on atomic coordinates in order to compare major features present in the 2D patterns
+		\item We can predict ionic conductivity using two agreeing methods -- Collective diffusion and nernst einstein
 	\end{itemize}
@@
 	HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16.
-All molecular dynamics simulations were run using Gromacs version 5.1.2.
+All molecular dynamics simulations were run using Gromacs version 5.1.2 and Gromacs version 2016.
 
@@
 		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
-		\item Manual modifications to the structure were made to create specific geometries
+		\item Manual modifications to the structure were made to create specific geometries for xray diffraction experiments
 	\end{itemize}
@@
 I can't think of a thesis for a figure that is purely illustrative
-	Each pore is made of twenty stacked monomer layers with continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
+	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
 	\begin{itemize}
@@
 		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
-
 	\begin{figure}
@@
 		\item TEM images and rejection studies give a pore size estimate
+	\end{itemize}
 
-	To prevent unrealistic jumps caused by poor atom placement during early equilibration steps, the following equilibration scheme was adopted.
+	An equilibration scheme with position restraints placed on benzene rings prevents unrealistic jumps during early equilibration steps.
 		\begin{itemize}
 			\item Apply position restraints to monomer head groups during energy minimization 
-			\item Leave position restraints for npt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
+			\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
 			\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
@@
 
-	Simulations of systems built by stacking monomers in the parallel-displaced and stacked configurations results in two different structures that are both stable for $>$ 500 ns, suggesting the existence of more than one metastable state.
+	Varying number of monomers in each stacked layer between 4 and 8, as well as the benzene stacking configuration between sandwiched and parallel displaced, results in multiple stable structures.
+        \begin{itemize}
+                \item We did a systematic study of the properties resulting from each starting configuration
+		\item Layers stacked 3.7 \AA apart based on WAXS
+		\item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions ~\ref{table:p2p}  % I think even six is too big.
+Leaving it in consideration though since the disordered version gives pretty good p2p distances
+		\item A characteristic of all systems was a defined, cylindrical and open pore structure.
+Benzene rings arrange in a helical conformation after equil.
+Membrane about 8 nm thick % BJC: maybe include thickness in the table?
+		\item Sandwiched and parallel-displaced configurations are both stable for 100's of nanoseconds and give reasonable xray diffraction patterns.
+		\item Free energy calculation to say which is more stable?
+		\item hypothesis: Parallel displaced is more stable and allows the benzene rings to stack closer together  
+	\end{itemize}
+
+	\begin{center}
+	\begin{tabular}{|c|c|}
+	\hline
+	table & here \\
+	\hline
+	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}
+	\end{tabular}
+	\end{center}
+
+	%BJC: Simulations of systems built by stacking monomers in the parallel-displaced and stacked configurations results in two different structures that are both stable for $>$ 500 ns, suggesting the existence of more than one metastable state.
+	Simulations of systems built with layers stacked 5 \AA apart results in a pore structure characterized by high radial disorder
 	\begin{itemize}
 		\item There are distinct differences in the pore structures between each state (Fig ~\ref{fig:porestructures})
-		\item The stacked configuration results in a pore with high radial disorder. 
-		\item The parallel displaced configuration results in an open cylindrical pore.
-Benzene rings remain offset and form a helix.
-The membrane is thinner and the pore spacing is greater.
-Density stays the same (?)
+		\item Membrane thicker with a smaller p2p distance
+		\item Two metastable states?
 	\end{itemize}

### 2017-04-24 Ben_Manuscripts/Outlines/Paper1_Outline.tex
Outline consistent with current understanding

@@
 \documentclass{article}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+\usepackage{subcaption}
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
@@
 			\item What does the microscopic pore structure look like and how can we relate that to monomer design and transport?
+		\end{itemize}
 		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
@@
 
-% 	Each pore is made of twenty stacked monomer layers, the smallest number of layers possible without sacrificing the expected aligned hexagonal morphology.
-%         %MRS4: OK, but note that we will need to expand this to be enough convincing qualitative information.
-Could also use quantitaitve information about how far from the surface you see the effects of the surface.
-% 	\begin{itemize}
-% 		\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
-% 		\item 5 layers create micellar structure
-% 		\item Beyond 20 layers is unnecessary to get expected configuration
-% 		\item layers spaced far enough apart to avoid large energy repulsions but close enough to prevent disks slipping between one another ~ 5 angstroms works.
-% 		\item How far into membrane do we have to go to avoid effects of the surface (this is a TODO)
-% 	\end{itemize}
-%MRS3: what is the thesis? decide what each figure is attempting to communicate to the reader.
-%BJC3: Maybe i include this in the supplemental information.
-I don't think a picture of the initial configuration is actually that interesting or important.
-I can't think of a thesis for a figure that is purely illustrative
 	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
@@
 		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
+	\end{itemize}
+
 	\begin{figure}
-	\includegraphics{placeholder.tex}
+	\includegraphics{placeholder.png}
 		\caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
@@
 	\begin{itemize}
+		\item Equilibration scheme:
+		\begin{itemize}
 			\item Apply position restraints to monomer head groups during energy minimization 
@@
 
+	Simulated X-ray diffraction patterns were generated based on atomic coordinates to give a deeper understanding of the pore structure and spacing. 
+        \begin{itemize}
+               \item 3 dimensional fourier transformed electron density generates simulated 1D and 2D diffraction patterns
+               \item The 1D patterns are generated by spherical integration of the FT
+               \item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
+               \item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
+        \end{itemize}
+
+	% Ionic conductivity here probably
 	\section{Results and Discussion}
 
-	Varying number of monomers in each stacked layer between 4 and 8, as well as the benzene stacking configuration between sandwiched and parallel displaced, results in multiple stable structures.
+        %\begin{wraptable}
+        %\begin{tabular}{|c|c|}
+        %\hline
+        %table & here \\
+        %\hline
+        %\end{tabular}
+        %\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}
+        %\end{wraptable}
+
+	Varying number of monomers in each stacked layer between 4 and 8, as well as the benzene stacking configuration between sandwiched and parallel displaced, results in more than one stable structures.
         \begin{itemize}
                 \item We did a systematic study of the properties resulting from each starting configuration
-		\item Layers stacked 3.7 \AA apart based on WAXS
+		\item In the real system, layers are stacked 3.7 \AA apart based on WAXS data. Pore spacing should be $ \approx 4.1 nm $
 		\item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions ~\ref{table:p2p}  % I think even six is too big.
 Leaving it in consideration though since the disordered version gives pretty good p2p distances
-		\item A characteristic of all systems was a defined, cylindrical and open pore structure.
+		\item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure.
 Benzene rings arrange in a helical conformation after equil.
-Membrane about 8 nm thick % BJC: maybe include thickness in the table?
+Membrane about 8 nm thick (Fig ~\ref{fig:phaseA}) % BJC: Still trying to prove that layered is trying to go towards a helical conformation.
+Also, maybe include thickness in the table?
+		\item This will be called phase A for simplicity  % BJC: I can come up with better phase names if that's important
 		\item Sandwiched and parallel-displaced configurations are both stable for 100's of nanoseconds and give reasonable xray diffraction patterns.
-		\item Free energy calculation to say which is more stable?
 		\item hypothesis: Parallel displaced is more stable and allows the benzene rings to stack closer together  
@@
 
-	\begin{center}
-	\begin{tabular}{|c|c|}
-	\hline
-	table & here \\
-	\hline
-	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}
-	\end{tabular}
-	\end{center}
+%	\begin{wraptable}
+%	\begin{tabular}{|c|c|}
+%	\hline
+%	table & here \\
+%	\hline
+%	\end{tabular}
+%	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}
+%	\end{wraptable}
 
 	%BJC: Simulations of systems built by stacking monomers in the parallel-displaced and stacked configurations results in two different structures that are both stable for $>$ 500 ns, suggesting the existence of more than one metastable state.
-	Simulations of systems built with layers stacked 5 \AA apart results in a pore structure characterized by high radial disorder
+	Simulations of systems built with layers stacked 5 \AA apart results in a pore structure characterized by high radial disorder.
 	\begin{itemize}
-		\item There are distinct differences in the pore structures between each state (Fig ~\ref{fig:porestructures})
-		\item Membrane thicker with a smaller p2p distance
-		\item Two metastable states?
+		\item This will be called phase B (~\ref{fig:phaseB})
+		\itme The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be fit to a gaussian distribution % BJC: supplemental info probably
+		\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the starting configuration
+		\item The phase is also present when phase A is heated close to its isotropic transition point
+		\item There are distinct differences in the membrane and pore structures between each state (Fig ~\ref{fig:porestructures})
+		\begin{itemize}
+			\item Phase B has a closed pore, while phase A is open. This will impact transport mechanisms
+			\item Phase B membranes are thicker
+			\item Consequently, the pore spacing is smaller
+		\end{itemize}
+		\item We have at least two metastable states
 	\end{itemize}
@@
 	\centering
-	\includegraphics{placeholder.pdf}
-		\caption{Different pore structure are clear between systems built with benzene rings layered in a (a) stacked or (b) parallel-displaced conformation}
+	\begin{subfigure}{.45\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{~\label{fig:phaseA}}
+	\end{subfigure}
+	\begin{subfigure}{.45\textwidth}
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\centering
+		\caption{~\label{fig:phaseB}}
+	\end{subfigure}
+	\caption{Different pore structure are clear between systems built with benzene rings stacked (a) 3.7 \AA apart and (b) 5.0 \AA apart}
 	\label{fig:porestructures}
@@
 	\begin{itemize}
-		\item Stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock
-		\item Those reflections are present from the 2D 
-%	Appropriate selection of initial structural parameters including interlayer spacing, relative interlayer orientation, and pore spacing results in an equilibrated model that is experimentally consistent.
-%	\begin{itemize}
-%		\item Visual perspective \\
-%MRS3: what is the thesis of the figure -- what is it trying to show.  Important when analyzing the outline and deciding what it means.  Make that the caption.
-%		FIGURE: shows top view and cross section (with pbcs on)\\
-%		caption: \\ 
-%		(a) The expected hexagonal membrane morphology is preserved upon equilibration \\
-%		(b) Straight cylindrical pore regions are present \\
-%		\item System dimensions and properties are consistent upon equilibration using multiple monomer configurations 
-%		\item Pore to pore distance
-%		\begin{itemize}
-%			\item We know from SAXS data what the distance between pores should be
-%			\item We require long simulation times to reach an equilibrated structure with the correct dimensions
-%			\item Crosslinking locks in structure, maintaining pore distances even after long simulations
-%		\end{itemize}
-
-%		FIGURE - 2 panels \\
-%		(a) Measuring the distance between pores over time indicates equilibration when the distances stop changing \\
-%		(b) A crosslinked system run for 100 ns shows that the system maintains itself close to its initial position \\
-
-%		\item Simulated X-ray Diffraction
-%		\begin{itemize}
-%			\item We used the 3 dimensional fourier transformed electron density to generate simulated 1D and 2D diffraction patterns
-%			\item The 1D patterns are generated by spherical integration of the FT
-%			\item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
-%			\item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
-%		\end{itemize}
-%	        
-		FIGURE - 4 panels \\
-        	(a) Experimental Small Angle X-ray Scattering data confirms a hexagonally packed morphology and tells us the average distance between pores \\
-        	(b) A simulated 1D x-ray diffraction pattern generated from atomic coordinates matches experimental measurements \\
-        	(c) Experimental Wide Angle X-ray Scattering patterns provide details of structure on a length scale less than 1 nm.
-The diffuse ring at q = 1.4 A\textsuperscript{-1} represents the average distance between carbons in packed alkyl chains.
-Meridional reflections at q = TBD A\textsuperscript{-1} are caused by pi-stacking.
-The weak meridional reflections at q = TBD A\textsuperscript{-1} are hypothesized to be a consequence of parallel-displaced stacking of benzene rings \\
-		(d) Simulated X-ray diffraction pattern show the same dominant reflections which appear experimentally
-
-		\item Pore Radius - a less reliable validation because we don't have an agreed upon way to measure this parameter experimentally
-		\item Density - there are crude lab measurements which my model is in agreement with (no one has reported any values since it wasn't relevant to them)
+		\item Phase A
+		\begin{itemize}	
+			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
+			\item There is evidence that the stacked configuration will shift towards an offset configuration over time.
+WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
+			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
 		\end{itemize}
-
-        Experiments to be run!
-%MRS4: more generally, we may want to explore the fact that there are other stable configurations (like the disordered ones we have found).
-We should brainstorm ways of calculating the free energy difference, BUT we should avoid it in this paper.
+		\item Phase B
 		\begin{itemize}
-                   \item Layered vs. offset configuration
-                   \begin{itemize}
-                        \item All simulations involving 'offset' configurations (which seems to be the correct configuration) will have a 'layered' counterpart in order to highlight difference between the two configurations.
-%MRS4: Which, hopefully, will show that that is not consistent with experiment.
-                        \item The comparison can be a figure in supplemental information
-                   \end{itemize}
-                   \item Measures of stability / analysis (These methods will be applied to all simulations run)
-                   \begin{itemize}
-                        \item Pore-to-pore distances
-                        \item Tilt angle vs. time  % it seems more likely that the circular anisotropy is NOT tilt angle but it is worth monitoring for now.
-                        \item Radial distribution functions  %MRS: this may be some thing that we present as an analysis AFTER we look at stability, since the other things are more things that can be verified vs.
-experiment.
-                        \item Simulated diffraction patterns
-                   \end{itemize}
-                   %MRS4: so this is something that we want to be careful about how we present the rationale.
-THe original rationale is that if the interactions were effectively too weak compared to experiemnt, then the 'effective' temperature would be a bit higher than we the 'thermostatted' temperature.
-I think that
-                   \item Effect of temperature on stability of configurations.
-15 degrees off (room temperature is 295) is much more likely than 260, though for our purposes, we probably want to run lower just to be sure.
-Would be interesting to know the temperature stability of the experimental structure before cross-linking .
-.
-.
-                   \begin{itemize}
-                        \item Three different temperature systems have been set up and simulated for 20 ns (All with 20 layers and no vapor gap): 260K, 280K and 300K
-                          %MRS4: we will need longer than 20 ns to make sure they have stabilized.  We know there are structures that are at least metastable (our somewhat more disordered phase)
-                        \item I have systems with no restraints on at all three temperatures
-                        \item We can look at them with weak restraints in case the systems misbehave as time goes on. As of now, the tilt angles look to stabilize after 10 ns
-%MRS4: yea, the reason for weak restraints would be to kind of replace the force field errors -- i.e.
-what would it look like if it HAPPENED to have a slightly larger bias toward that configuration.
-Ideally, we won't need restraints.
-%MRS4: and maybe we do it with just the 3 temperatures first, before adding restraints.
-THere are so many variables, we want to be sure we are running simulations which are more likely to give results.
-                        \item If we get stable configurations with correct XRD patterns at lower temps but not higher, it may be a consequence of the forcefield %MRS: correct, though it's better if it works ok at 280 vs 260.
-We don't want it to start to crystallize.
-                        \end{itemize}
-                   \item Effect of restraints on stability
-		   \begin{itemize}
-                        \item Run out simulations with weak restraints (f = 0.1 kJ/mol*nm2) %MRS4: or possibly weaker.
-Should work out the RMSD allowed by the restraints, and possibly let them move as much as 1/6 of the way around the circle.
-                        \item Higher restraints may cause the system to be too ordered, but it may be worth running in the case of long term movement
-                        \item Run out simulations with no restraints (same simulation as 300K, no restraints from temperature stability sims)
-                        \item Hopefully this will let us abandon restraints after equilibration
-                   \end{itemize}
-		   \item Other simulations
-                   \begin{itemize}
-                     %MRS4: OK, so this is the same as above, except with no tilt in the monomers?
-                        \item Offset, no vapor gap, 20 layer : No tilt (i.e.
-use monomers that I have previously used).
-I want to see if the diagonal spots still show up.
-The concern here is that I wont be able to get the monomers close enough together without causing some unreconcilable energy minimization errors.
-%MRS4: it is good to see if spots an appear from the tilt, though it looks like we can get them with layered configurations even w/o the tilt.
-                        \item Offset, higher tilt.
-I'm working on a monomer that tilted more than the one I previously used.
-Can I make spots appear based purely on tilt?
-Also, what implications does this have for the pore spacing.
+			\item Stacking refelctions present indicating separation of $ \approx 5 \AA $
+			\item No spots at all which is consistent with the disorder shown by the rings in the pore
 		\end{itemize}
@@
 
-	The monomers are arranged into disks containing 5 monomers in each layer.
-	%BJC: So, it looks like there is some kind of z directional order 
-       	%BJC5: This will require some re-evaluation once we come to a reliable starting configuration and equilibration procedure based on the diffraction results
+	\begin{figure}
+	\centering
+	\begin{subfigure}{.3\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{~\label{fig:xrdA}}
+	\end{subfigure}
+	\begin{subfigure}{.3\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{~\label{fig:xrdexp}}
+	\end{subfigure}
+        \begin{subfigure}{.3\textwidth}
+                \centering
+                \includegraphics[width=\linewidth]{placeholder.png}
+                \caption{~\label{fig:xrdB}}
+        \end{subfigure}
+	\caption{Phase A (a) provides a good match to experiment (b). Phase B (c) is missing reflections present in the experimental pattern}
+	\label{fig:xrd}
+	\end{figure}
 
-	\begin{itemize}
-		\item It has been suggested that there are 4 monomers in a each disk/layer, however, simulations have shown that this leads to unstable configurations with dimensions that are too small compared to experiment.
-		\item Stable simulations with 6 and 7 monomers have been performed which give structural characteristics consistent with experiment
-		\item Stable systems have also been simulated consisting of varying numbers of monomers per layer
-		\item Calculating the number density of components in the z direction has shown defined groups % will do for 7 monomers / layer and alternating monomers / layer
-		\\ Figure \\
-		(a) The number density of benzene ring centers in the z direction shows regions with higher concentrations of the component \\
-		(b) A power spectrum of the data in (a) indicates that a new layer is defined every 4 angstroms implying that there are 5 monomers per layer.\\
-%MRS4: make it clear that this is calculated from the equilbrium distance. 
-%MRS5: in general, there should be some information we can see looking directly at the density, not just the power spectrum.  We will need to convince people there is something there.
-		\item Even though there are defined regions of higher component density, there is still considerable variation in the position of the components (shown by the extra noise in the power spectrum)
-		\item This suggests that the arrangement of monomers is more complicated than simple layers stacked on top of each other
-		\item Density of components along Z axis \\
-%MRS4: we need to reconcile the idea ``there are 5 monomers per layer'' and ``there are not clear layers''.  It will be hard for me to reconcile them without knowing a bit more information.
-%BJC5: Hopefully I'll have an answer to this soon. For now I'm leaving it untouched
-		\item There are not clear layers despite the defined layers in the starting configuration.
-
-	\end{itemize}
-
-	The arrangement of sodium counterions within the hydrophilic pore regions can be fit to a gaussian distribution. 
-	\begin{itemize}
-		\item Past literature reports ions arranged in a circle about pore walls implying some kind of void space as a pore.
-Simulations under a variety of conditions suggest that ions prefer disorder within the pores.
-		\item A size exclusion mechanism has been proposed in the past, however that might no be the only force at play
-		\item Ions may play a role in transport, hindering flux of solute and solvent by slowing their diffusion
-		\item The membrane may exhibit the permeability-selectivity tradeoff inherent to solution-diffusion type membranes.
-		\\FIGURE - plot from grant - sodium, benzene, tail densities in pores
-                %MRS3: again, thesis.
-%MRS4: we should think a little bit about whether which parts of the alkyl tail we plot, and whether to just focus on the core (ignoring the first 5 A or so from each end).
-Depends on what we are trying to show.
-		caption: The densities of sodium (blue), benzene (red), and alkyl tail carbons (cyan) surrounding the membrane pore centers indicate that each the pore region is a soup of the three components opposing the previously assumed hollow region.
-	\end{itemize}
-
-	%BJC: New x-ray data here. Need higher resolution simulated data (working on it) and supporting experimental results first.
-        %MRS4 got it.  Will need to do some work on making this clear.
+	%BJC: generated 1D SAXS somewhere?? Just to show that we get the spacing right
 
@@
 		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
-		\item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system
-                %MRS4: not sure you describe how to do that here.
-		%BJC5: We should discuss how we will actually make the link.
+		\item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system. %BJC: worth getting into? See comment below.
+		%BJC: We should discuss how we will actually make the link.
 We talked about it once but kind of left it hanging.
@@
 		\item Two methods used to for prediction
+		%BJC: probably belongs in methods:
 		\item Nernst Einstein Relation:
@@
 		\end{itemize}
-		\item Collective Diffusion:
+		\item Collective Diffusion:  %BJC: will leave explanation of how I did it for supplemental info (so most of the following). Will just reference paper
 		\begin{itemize}
@@
 	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies.
-Using the design framework and analysis methods applied herin, we have the ability to reliably predict properties of new nanoporous membranes.
+Using the design framework and analysis methods applied herin, we have the ability to reliably predict structures of new nanoporous membranes.
 
@@
 	\begin{itemize}
-		\item show all pore-to-pore equilibration plots used to prove independence of starting conifiguration
+		\item Pore-to-pore equilibration plots
 		\item 3D visualizations of different configurations tested
-		\item 7 monomer per layer configurations and others if needed.
+		\item Table of measurements on 5-8 monomer per layer configurations
+		\item Sodium ion distribution in disordered phase
 	\end{itemize}

### 2017-04-25 Ben_Manuscripts/Outlines/Paper1_Outline.tex
up to date outline

@@
 \usepackage{subcaption}
+\usepackage{geometry}
+\geometry{legalpaper, margin=1in}
+\usepackage{amsmath} % or simply amstext
+\newcommand{\angstrom}{\textup{\AA}}
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
@@
 	\begin{itemize}
-		\item XRD gives Pore-to-Pore distances of ~4.1 nm and indicates possible pi-stacking at ~3.7 Angstroms (see figure blah blah later on - comparison of experimental vs. simulated)
+		\item XRD gives Pore-to-Pore distances of $\approx$ 4.1 nm and indicates possible pi-stacking at $\approx$ 3.7 \angstrom (see figure~\ref{fig:xrd}) on - comparison of experimental vs. simulated)
 		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
 		\item T-shaped and parallel-displaced are nearly isoenergetic and more stable than the sandwiched configuration.
-		\item T-shaped configuration is most stable when benzene centers are ~ 5 A apart which is not consistent with WAXS. http://www.jbc.org/content/273/25/15458.full 
+		\item T-shaped configuration is most stable when benzene centers are $\approx$ 5 \angstrom apart which is not consistent with WAXS. % http://www.jbc.org/content/273/25/15458.full 
 		\item System made with stacked and parallel-displaced benzene rings to see what is favored and matches XRD
@@
 
-        %\begin{wraptable}
-        %\begin{tabular}{|c|c|}
-        %\hline
-        %table & here \\
-        %\hline
-        %\end{tabular}
-        %\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}
-        %\end{wraptable}
-
 	Varying number of monomers in each stacked layer between 4 and 8, as well as the benzene stacking configuration between sandwiched and parallel displaced, results in more than one stable structures.
@@
                 \item We did a systematic study of the properties resulting from each starting configuration
-		\item In the real system, layers are stacked 3.7 \AA apart based on WAXS data. Pore spacing should be $ \approx 4.1 nm $
-		\item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions ~\ref{table:p2p}  % I think even six is too big.
+		\item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. Pore spacing should be $\approx$ 4.1 nm
+		\item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Fig~\ref{table:p2p})  % I think even six is too big.
 Leaving it in consideration though since the disordered version gives pretty good p2p distances
@@
 
-%	\begin{wraptable}
-%	\begin{tabular}{|c|c|}
-%	\hline
-%	table & here \\
-%	\hline
-%	\end{tabular}
-%	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}
-%	\end{wraptable}
+	%\begin{wraptable}{m}{5.5cm}
+	\begin{table}
+	\centering
+	\begin{tabular}{|c|c|}
+	\hline
+	table & here \\
+	\hline
+	\end{tabular}
+	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}
+	\end{table}
+	%\end{wraptable}
 
 	%BJC: Simulations of systems built by stacking monomers in the parallel-displaced and stacked configurations results in two different structures that are both stable for $>$ 500 ns, suggesting the existence of more than one metastable state.
-	Simulations of systems built with layers stacked 5 \AA apart results in a pore structure characterized by high radial disorder.
+	Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
 	\begin{itemize}
-		\item This will be called phase B (~\ref{fig:phaseB})
-		\itme The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be fit to a gaussian distribution % BJC: supplemental info probably
+		\item This will be called phase B (Fig~\ref{fig:phaseB})
+		\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be fit to a gaussian distribution % BJC: supplemental info probably
 		\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the starting configuration
 		\item The phase is also present when phase A is heated close to its isotropic transition point
-		\item There are distinct differences in the membrane and pore structures between each state (Fig ~\ref{fig:porestructures})
+		\item There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
 		\begin{itemize}
@@
 	\end{subfigure}
-	\caption{Different pore structure are clear between systems built with benzene rings stacked (a) 3.7 \AA apart and (b) 5.0 \AA apart}
+	\caption{Different pore structure are clear between systems built with benzene rings stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
 	\label{fig:porestructures}
@@
 		\begin{itemize}
-			\item Stacking refelctions present indicating separation of $ \approx 5 \AA $
+			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
 			\item No spots at all which is consistent with the disorder shown by the rings in the pore
@@
 		\end{itemize}                    
+		\item See comparison of methods in Table~\ref{table:conductivity}
 	\end{itemize}
-	TABLE: Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error
-	\\
+
+	\begin{table}
+	\centering
+	\begin{tabular}{|c|c|}
+	\hline
+	Nernst Einstein & Collective Diffusion \\
+	\hline
+	\end{tabular}
+	\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error~\label{table:conductivity}}
+	\end{table}
 

### 2017-04-25 Ben_Manuscripts/Outlines/Paper1_Outline.tex
updates

@@
 
+	Questions to answer from here:
+	\begin{itemize}
+		\item What is the relative stability of the disordered vs ordered state? (Free energy calculation)
+		\item Which phase is prevalent across a range of temperatures? Can replica exchange tell us what where the system prefers to spend its time?
+		\item Do we observe both phases experimentally? (would be nice but probably not feasible for our timeline without some luck)
+	\end{itemize}
+
 	The model gives reasonable estimates of ionic conductivity.

### 2017-04-27 Ben_Manuscripts/Outlines/Paper1_Outline.tex
comments on outline.

--- 2017-04-25 Ben_Manuscripts/Outlines/Paper1_Outline.tex
@@
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
+%MRS: we probably will want to add in Glaser's student (and possibly glaser) for their work on the X-ray simulations.
+%MRS: also possibly Xunda if we end up using X-ray diffraction images of theirs that are not published.
 \begin{document}
@@
 		\item Many current RO membranes degrade in typical chlorine filled municipal water supplies (debating this point because there aren't any studies of LLC membrane fouling resistance)
+                  %MRS: Doug should have information on the chemistry here and how resistant they might be.
 		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
@@
 Rejection studies show that this membrane can not do desalination yet
+%MRS: ^^^nice way to turn a weakness of the materials class into an opportunity to improve them requring research! 
 		\item Colh phase studies currently limited to one monomer
@@
                         \item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
+                          %MRS: vvv this point below should be made more specific.  Ionic gradient at the end?  Donnan exclusion?
                         \item Does concentration of ions in the pore repel incoming ions?
-                        \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection
+                        \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
+                         %MRS: vvv can you be a bit more specific about ``transport barriers?''
                         \item Is water structured inside the pores leading to transport barriers?
+                          %MRS: vvv maybe put this higher, since the other bullet points above are dependent on this.
+Also, this point conflacts understanding the structure, and then modifying it, which are sort of two steps.
 			\item What does the microscopic pore structure look like and how can we relate that to monomer design and transport?
@@
 
-	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, will confirm or deny past drawn conclusions that have largely guided our understanding of separation mechanisms.
+	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, 
+%MRS: a molecular model can't really confirm or deny, because of the approximations.  provide evidence to support or call into question previous conclusions.
+will confirm or deny past drawn conclusions that have largely guided our understanding of separation mechanisms. 
 	\begin{itemize}
@@
 			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer 
+                          %MRS: vvv this point has a partial answer as well as a question -- do you want that here?
 			\item Does the equilibrated structure exist in distinct layers? Fourier analysis can help answer this question
@@
 	\begin{itemize}
+          %MRS: ``careful'': better to show, not tell that it is careful.
 		\item This paper will illustrate the careful development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
@@
 		\item We are primarily interested in reproducing the conclusions about structure which have been made from XRD experiments and ionic conductivity measurements.    
+                  %MRS: algorithm not really the main finding.
 		\item We have written an algorithm to simulate the crosslinking mechanism and understand its influence on membrane structure
+                  %MRS: the fact that we can is not that much interest, rather that we do.  Restate along lines of ``we havecompared simulated x-ray diffraction to experiment''
 		\item We can simulate x ray diffraction patterns based on atomic coordinates in order to compare major features present in the 2D patterns
@@
 		\item Antechamber used for atomtyping with gaff forcefield
-		\item Used Openeye Quacpac molcharge.py to assign charges
+		\item Used Openeye Quacpac molcharge.py to assign charges %MRS: explain reason for 2 charge steps.
 		\item Anneal again 
@@
 	\end{itemize}
-
+%MRS: justify choice of 20?	
 	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
@@
 	\begin{figure}
+          %MRS: this probably isn't so important it should be a figure in the main paper (maybe supporting).
 	\includegraphics{placeholder.png}
@@
 		\item This will be called phase A for simplicity  % BJC: I can come up with better phase names if that's important
+%MRS: I though sandwitched not that stable?
 		\item Sandwiched and parallel-displaced configurations are both stable for 100's of nanoseconds and give reasonable xray diffraction patterns.
@@
 	\end{tabular}
-	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}
+	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will%MRS: maybe not be the most stable? 
+not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}  
 	\end{table}
@@
 		\item This will be called phase B (Fig~\ref{fig:phaseB})
-		\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be fit to a gaussian distribution % BJC: supplemental info probably
+		\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be fit to a gaussian distribution % BJC: supplemental info probably %MRS: anything can be fit to.
+Do you mean well-approximated by?
 		\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the starting configuration
@@
 	\end{figure}
-
+%MRS: probably should point out things that both models get right, like the C-C isotropic band.
 	Comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration
@@
 			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
+%MRS: just wondering, are the offset configurations pi-stacking distances closer than the direct stacking ones?  Seem like might be.
 		\end{itemize}
@@
 	%BJC: generated 1D SAXS somewhere?? Just to show that we get the spacing right
-
+        %MRS: reasonable estimates for which structure?
 	The model gives reasonable estimates of ionic conductivity.
@@
 
+	%MRS: seems like needs to be a bit more discussion about 5 vs 6 vs 7, and which is most likely? 
+        %MRS: will have to discuss a bit more about pi-stacking in GAFF and in reality, and how we might expect that will chage things.
+
 	\section{Conclusion}
@@
 		\item Channels are more disordered than previously thought and are filled with organic matter rather than hollow 
+                  %MRS: vvvv this is true even for parallel displaced?
 		\item There are likely no defined layers
@@
 		\item Pore-to-pore equilibration plots
+                  %MRS: ^^^ probably should include how we determined if we ran long enough.
 		\item 3D visualizations of different configurations tested
+                  %MRS: vvv this might be in the main text, since it is what allows us to say what is more likely.
 		\item Table of measurements on 5-8 monomer per layer configurations

### 2017-04-27 Ben_Manuscripts/Outlines/Paper1_Outline.tex

@@
 	%BJC: generated 1D SAXS somewhere?? Just to show that we get the spacing right
+
+        %MRS: Not clear what ``questions to answer from here'' means.
+If it's questions beyond the scope of the paper, should go in discussion.
+Rephrase to be clearer thesis topic.
+Or is this just notes for us?
+	Questions to answer from here:
+	\begin{itemize}
+		\item What is the relative stability of the disordered vs ordered state? (Free energy calculation)
+		\item Which phase is prevalent across a range of temperatures? Can replica exchange tell us what where the system prefers to spend its time?
+		\item Do we observe both phases experimentally? (would be nice but probably not feasible for our timeline without some luck)
+	\end{itemize}
+
         %MRS: reasonable estimates for which structure?
+
 	The model gives reasonable estimates of ionic conductivity.

### 2017-04-27 Ben_Manuscripts/Paper1/methods.tex

--- 2017-04-25 Ben_Manuscripts/Outlines/Paper1_Outline.tex
@@
-\documentclass{article}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{geometry}
-\geometry{legalpaper, margin=1in}
-\usepackage{amsmath} % or simply amstext
-\newcommand{\angstrom}{\textup{\AA}}
-\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
-\begin{document}
-	\bibliographystyle{ieeetr}
-	\graphicspath{{./figures/}}
-	\maketitle
-	\section{Introduction}
-	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale allowing design of solute-specific separation membranes.
-	\begin{itemize}
-		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
-		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
-		\item Designing RO membranes to achieve targeted separations of specific solutes is nearly impossible due to the separation (hypothesized to be) controlled by fluctuating polymer voids
-		\item RO has difficulty separating neutral organics because they tend to dissolve in polymer matrix
-		\item Many current RO membranes degrade in typical chlorine filled municipal water supplies (debating this point because there aren't any studies of LLC membrane fouling resistance)  
-		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
-		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
-		\item Entirely different mechanisms govern the separation processes in various nanostructured materials which can inspire novel separation techniques
-	\end{itemize}
-
-	Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
-	\begin{itemize}
-		\item Leading technologies and their limitations:
-		\begin{itemize}
-			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact selectivity
-			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
-			%BJC: The following are ideas pulled from the grant. I need to do some reserach and come up with some one liners as to why each have not been successful
-			\item Track-etch membranes
-		    	\item Molecular squares
-			\item Macrocyclic surfactants 
-		\end{itemize}
-	\end{itemize}
-
-	Self assembling lyotropic liquid crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques feasible for large scale production.
-	\begin{itemize}
-		\item LLCs are versatile and controllable with a large chemical design space available for membrane design
-		\item Synthetic techniques are cheap and amenable to creating any monomer in this large design space
-		\item LLCs forms lamellar, bicontinuous cubic and hexagonal phases based on solution composition
-		\item Na-GA3C11 has been described in literature as forming two types of self assembled phases - thermotropic (Colh) and lyotropic (HII)
-		\item The thermotropic, Colh, is formed by the self assembly of neat monomer
-		\item The lyotropic, HII phase is formed in the presence of small amounts of water
-		\item Both assemble into cylinders with hydrophilic groups oriented inward towards the pore center and hydrophobic groups facing outward.
-The only difference is the inclusion of water in the structure which leads to minor variations in the structure with potentially different filtration properties (although no filtration experiments have been done on Colh)
-		\item Hydrophilic regions point towards pore centers
-		\item Until recently, they could not be aligned - hindered progress
-		\item Yale aligns them, then crosslinks them to lock in the structure - reference 2014 and 2016 papers. They say that they are scalable techniques
-		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
-		\item The Colh phase shares the same structural features with the HII phase with the exception of the presence of water.
-This paper will focus on the development of a model of the Colh phase since it is a simpler starting point and has just as much experimental data.
-The analysis used in this paper can be readily extended to the HII phase.
-	\end{itemize}
-
-	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines to reduce the chemical space for design of monomers used to create separation-specific membranes.
-	\begin{itemize}
-                \item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effective water desalination and small organic separations.
-Rejection studies show that this membrane can not do desalination yet
-		\item Colh phase studies currently limited to one monomer
-                \item Optimization efforts performed through trial and error over the past 20 years
-                \item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
-                \begin{itemize}
-                        \item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
-                        \item Does concentration of ions in the pore repel incoming ions?
-                        \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection
-                        \item Is water structured inside the pores leading to transport barriers?
-			\item What does the microscopic pore structure look like and how can we relate that to monomer design and transport?
-		\end{itemize}
-		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
-		\item We can use molecular dynamics simulations to enhance our understanding 
-	\end{itemize}
-
-	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, will confirm or deny past drawn conclusions that have largely guided our understanding of separation mechanisms.
-	\begin{itemize}
-		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
-		\begin{itemize}
-			\item This could change how one thinks about molecules diffusing through membrane
-			\item Could also be a difference between lyotropic and thermotropic phases
-		\end{itemize}
-		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
-		\begin{itemize}
-			\item How do the monomer head groups pack together? Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
-			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
-			\item Substituted benzene preferred stacking mode? Learning more about this   	
-			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
-			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer 
-			\item Does the equilibrated structure exist in distinct layers? Fourier analysis can help answer this question
-		\end{itemize}
-		\item It is possible there is more than one metastable states associated with this LLC system
-		\begin{itemize}
-			\item Which phase is consistent with experiment?
-			\item Can both phases be created experimentally?
-			\item How will each state affect transport?
-		\end{itemize}
-	\end{itemize}
-
-	We must show that the developed molecular model is consistent with physical observations so that we can trust conclusions drawn about structural features characteristic of the system.
-	\begin{itemize}
-		\item This paper will illustrate the careful development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
-		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
-		\item We are primarily interested in reproducing the conclusions about structure which have been made from XRD experiments and ionic conductivity measurements.    
-		\item We have written an algorithm to simulate the crosslinking mechanism and understand its influence on membrane structure
-		\item We can simulate x ray diffraction patterns based on atomic coordinates in order to compare major features present in the 2D patterns
-		\item We can predict ionic conductivity using two agreeing methods -- Collective diffusion and nernst einstein
-	\end{itemize}
-
 \section{Methods}
 
-	HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16.
-All molecular dynamics simulations were run using Gromacs version 5.1.2 and Gromacs version 2016.
+HII monomers were parameterized using the Generalized Amber Forcefield
+with the Antechamber package provided with AmberTools16. Charges were
+assigned using tools from Openeye Scientific Software. All molecular dynamics
+simulations were run using Gromacs version 5.1.2 and Gromacs version 2016.
 
-	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
-	\begin{itemize}
-		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
-		\item Result not global minimum but close enough for structure building
-		\item Antechamber used for atomtyping with gaff forcefield
-		\item Used Openeye Quacpac molcharge.py to assign charges
-		\item Anneal again 
-		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
-		\item Manual modifications to the structure were made to create specific geometries for xray diffraction experiments
-	\end{itemize}
+An ensemble of characteristic, low-energy vacuum monomer configurations
+were constructed by applying a simulated annealing process to a
+parameterized monomer. Monomers were cooled from 1000K to 50K over 10
+nanoseconds. A low energy configuration was pulled from the trajectory 
+and charges were reassigned using the am1bccsym method of molcharge
+shipped with Openeye Scientific software's QUACPAC. Using the new
+charges, the monomer system was annealed again and multiple monomer
+configurations were pulled from the trajectory.
 
-	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for a more efficient way to build the system.
-	\begin{itemize}
-		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
-		\item Attempts with Colh system not fruitful  
-		\begin{itemize}
-			\item Packed monomers into box
-			\item Simulated for ~100 ns with no progress shown towards self assembly
-		\end{itemize}  
-		\item Wrote code to assemble monomers into Colh configuration close to what is expected 
-		\item Equilibration simulations allow structure to relax into expected configuration 
-	\end{itemize}
+The timescale for self assembly of monomers into the hexagonal phase is
+unknown and likely outside of a reasonable length for an atomistic
+simulation, calling for a more efficient way to build the system. 
+Previous work has shown a coarse grain model self assemble into the HII
+phase configuration in $\approx$ 1000 ns. Atomistic self-assembly was 
+attempted by packing monomers into a box using Packmol. Simulations of >
+100 ns show no progress towards an ordered system. To bypass the 
+slow self-assembly process, python code was written in order that 
+assembles monomers into a configuration close to the expected 
+equilibrium configuration. A short, restrained equilibration, followed 
+by NPT simulations > 500 ns, allows the initial configuration to relax
+into an equilibrium configuration.
 
-	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
-	\begin{itemize}
-		\item A thinner system is better to reduce the computational cost and allow us to look at longer timescales
-		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
-	\end{itemize}
+Each pore consists of twenty stacked monomer layers with periodic 
+continuity in all directions, avoiding any edge effects and creating an
+infinite length pore ideal for studying transport
+(Fig.~\ref{fig:initial}). A small number of layers is preferred in order
+to reduce computational cost and to allow us look at longer timescales.
+Ultimately, we chose to build a system with 20 layers of monomer in each
+pore in order to give sufficient resolution when simulating X-ray 
+diffraction patterns.
 
+% Questionably needed figure
 \begin{figure}
 \includegraphics{placeholder.png}
-		\caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
+	\caption{Monomers are placed in an initial configuration close to
+	         the expected equilibrium configuration and allowed to relax}
 	\label{fig:initial}
@@
 
-	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
-	\begin{itemize}
-		\item XRD gives Pore-to-Pore distances of $\approx$ 4.1 nm and indicates possible pi-stacking at $\approx$ 3.7 \angstrom (see figure~\ref{fig:xrd}) on - comparison of experimental vs. simulated)
-		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
-		\item T-shaped and parallel-displaced are nearly isoenergetic and more stable than the sandwiched configuration.
-		\item T-shaped configuration is most stable when benzene centers are $\approx$ 5 \angstrom apart which is not consistent with WAXS. % http://www.jbc.org/content/273/25/15458.full 
-		\item System made with stacked and parallel-displaced benzene rings to see what is favored and matches XRD
-		\item TEM images and rejection studies give a pore size estimate
-	\end{itemize}
+Initial guesses for the remaining structural parameters were chosen
+based on experimental data and treated as variables during model
+development. The distance between pores was based on experimental SAXS
+data for this system. Initial configuration pore spacing was chosen to
+be 10 \% larger than the experimental value. The layer spacing was based
+on reflections from experimental WAXS data at 3.7 \angstrom, thought to
+represent pi-stacking between stacked benzene rings. The tendency of 
+simulations to equilibrate to slightly larger interlayer spacing 
+inspired systems starting with layer spacings > 4 \angstrom.
+% There is plenty I can say about initial configuration. Starting layers
+% too far apart, too close, tilted initial configurations etc.
+The relative interlayer orientation was chosen based on the various 
+stacking modes of benzene and substituted benzene rings: sandwiched,
+T-shaped and parallel-displaced. The T-shaped configuration was ruled
+out based on the inconsistency of its preferred stacking distance of 
+$\approx$ 5 \angstrom, with diffraction data. The system's preference
+towards the sandwiched vs. parallel displaced stacking modes was left
+as a variable. Initial pore radius estimates were based on past TEM 
+images and size exclusion rejection data.
 
-	An equilibration scheme with position restraints placed on benzene rings prevents unrealistic jumps during early equilibration steps.
+An equilibration scheme with position restraints placed on benzene rings
+prevents unrealistic jumps during early equilibration steps. Restraints
+allow the system to remain in the sandwiched and parallel-displaced 
+configurations while monomer tails settle. Doing so also helps prevent
+system dependence on initial monomer configuration. During the restrained
+equilibration, force constants are reduced by the square root of the 
+previous force constant, with a starting value of 1e6.  by the
 \begin{itemize}
@@
 % Ionic conductivity here probably
-	\section{Results and Discussion}
-
-	Varying number of monomers in each stacked layer between 4 and 8, as well as the benzene stacking configuration between sandwiched and parallel displaced, results in more than one stable structures.
-        \begin{itemize}
-                \item We did a systematic study of the properties resulting from each starting configuration
-		\item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. Pore spacing should be $\approx$ 4.1 nm
-		\item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Fig~\ref{table:p2p})  % I think even six is too big.
-Leaving it in consideration though since the disordered version gives pretty good p2p distances
-		\item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure.
-Benzene rings arrange in a helical conformation after equil.
-Membrane about 8 nm thick (Fig ~\ref{fig:phaseA}) % BJC: Still trying to prove that layered is trying to go towards a helical conformation.
-Also, maybe include thickness in the table?
-		\item This will be called phase A for simplicity  % BJC: I can come up with better phase names if that's important
-		\item Sandwiched and parallel-displaced configurations are both stable for 100's of nanoseconds and give reasonable xray diffraction patterns.
-		\item hypothesis: Parallel displaced is more stable and allows the benzene rings to stack closer together  
-	\end{itemize}
-
-	%\begin{wraptable}{m}{5.5cm}
-	\begin{table}
-	\centering
-	\begin{tabular}{|c|c|}
-	\hline
-	table & here \\
-	\hline
-	\end{tabular}
-	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}
-	\end{table}
-	%\end{wraptable}
-
-	%BJC: Simulations of systems built by stacking monomers in the parallel-displaced and stacked configurations results in two different structures that are both stable for $>$ 500 ns, suggesting the existence of more than one metastable state.
-	Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
-	\begin{itemize}
-		\item This will be called phase B (Fig~\ref{fig:phaseB})
-		\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be fit to a gaussian distribution % BJC: supplemental info probably
-		\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the starting configuration
-		\item The phase is also present when phase A is heated close to its isotropic transition point
-		\item There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
-		\begin{itemize}
-			\item Phase B has a closed pore, while phase A is open. This will impact transport mechanisms
-			\item Phase B membranes are thicker
-			\item Consequently, the pore spacing is smaller
-		\end{itemize}
-		\item We have at least two metastable states
-	\end{itemize}
-
-	\begin{figure}
-	\centering
-	\begin{subfigure}{.45\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:phaseA}}
-	\end{subfigure}
-	\begin{subfigure}{.45\textwidth}
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\centering
-		\caption{~\label{fig:phaseB}}
-	\end{subfigure}
-	\caption{Different pore structure are clear between systems built with benzene rings stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
-	\label{fig:porestructures}
-	\end{figure}
-
-	Comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration
-	\begin{itemize}
-		\item Phase A
-		\begin{itemize}	
-			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
-			\item There is evidence that the stacked configuration will shift towards an offset configuration over time.
-WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
-			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
-		\end{itemize}
-		\item Phase B
-		\begin{itemize}
-			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
-			\item No spots at all which is consistent with the disorder shown by the rings in the pore
-		\end{itemize}
-	\end{itemize}
-
-	\begin{figure}
-	\centering
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:xrdA}}
-	\end{subfigure}
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:xrdexp}}
-	\end{subfigure}
-        \begin{subfigure}{.3\textwidth}
-                \centering
-                \includegraphics[width=\linewidth]{placeholder.png}
-                \caption{~\label{fig:xrdB}}
-        \end{subfigure}
-	\caption{Phase A (a) provides a good match to experiment (b). Phase B (c) is missing reflections present in the experimental pattern}
-	\label{fig:xrd}
-	\end{figure}
-
-	%BJC: generated 1D SAXS somewhere?? Just to show that we get the spacing right
-
-	Questions to answer from here:
-	\begin{itemize}
-		\item What is the relative stability of the disordered vs ordered state? (Free energy calculation)
-		\item Which phase is prevalent across a range of temperatures? Can replica exchange tell us what where the system prefers to spend its time?
-		\item Do we observe both phases experimentally? (would be nice but probably not feasible for our timeline without some luck)
-	\end{itemize}
-
-	The model gives reasonable estimates of ionic conductivity.
-	\begin{itemize}
-		\item There are a few ways to estimate ionic conductivity as seen in literature. We prefer a method which can extract an estimate based purely on an equilibrium trajectory
-		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
-		\item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system. %BJC: worth getting into? See comment below.
-		%BJC: We should discuss how we will actually make the link.
-We talked about it once but kind of left it hanging.
-It will likely be just some constant that we multiply our number by.
-To calculate the constant, I think using the azimuthal distribution is a good way to go about it.
-Although for that we'd need more data points telling us ionic conductivity as a function of azimuthal angle.
-That data will definitely be hard to come by in the near future so maybe a linear model is an okay estimate for now -- just to have something.
-For that, we know ionic conductivity with randomly oriented crystalline domains and we know ionic conductivity of a 'perfectly' aligned system (from our simulations).
-So we can make ionic conductivity as a linear function of alignment, I(x) (Actually it'd be piecewise with opposite slopes on either side of the an azimuthal angle of 90).
-Then we can integrate the azimuthal distribution weighted by I(x) to get a number to multiply our measurements by.
-		\item Two methods used to for prediction
-		%BJC: probably belongs in methods:
-		\item Nernst Einstein Relation:
-		\begin{itemize}
-			\item Widely used equation for estimating ionic conductivity
-			\item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
-			\item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
-			\item Concentration is concentration of ions in the whole membrane, not just channels
-		\end{itemize}
-		\item Collective Diffusion:  %BJC: will leave explanation of how I did it for supplemental info (so most of the following). Will just reference paper
-		\begin{itemize}
-			\item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
-			\item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
-			\item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
-			\item A similar model has been derived and validate to predict water permeability using equilibrium simulations
-			\item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores.
-One would expect single channel IC to be much larger than the bulk membrane
-		\end{itemize}                    
-		\item See comparison of methods in Table~\ref{table:conductivity}
-	\end{itemize}
-
-	\begin{table}
-	\centering
-	\begin{tabular}{|c|c|}
-	\hline
-	Nernst Einstein & Collective Diffusion \\
-	\hline
-	\end{tabular}
-	\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error~\label{table:conductivity}}
-	\end{table}
-
-	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies.
-Using the design framework and analysis methods applied herin, we have the ability to reliably predict structures of new nanoporous membranes.
-
-	\section{Conclusion}
-
-	In this work, we have suggested a more detailed picture of the structure of a self assembled thermotropic liquid crystal membrane using an atomistic molecular model.
-	\begin{itemize}
-		\item The model's physical properties are consistent with experimental measurements
-		\item Channels are more disordered than previously thought and are filled with organic matter rather than hollow 
-		\item There are likely no defined layers
-		\item Results presented for Colh phase monomer but methods are readily adapted to other LCs
-	\end{itemize}
-
-	\section{Supplemental Information}
-
-	Monomer configurations
-	\begin{itemize}
-		\item Pore-to-pore equilibration plots
-		\item 3D visualizations of different configurations tested
-		\item Table of measurements on 5-8 monomer per layer configurations
-		\item Sodium ion distribution in disordered phase
-	\end{itemize}
-
-	\noindent Crosslinking details
-	\begin{itemize}
-		\item Algorithm description. Link to full algorithm in git repository
-		\item A figure showing the new crosslinks
-	\end{itemize}
-
-	\noindent Ionic conductivity % plus more details on implementation.
-	\begin{itemize}
-		\item MSD plots
-	\end{itemize}
-\end{document}

### 2017-04-27 Ben_Manuscripts/Outlines/Paper1_Outline.tex
minor edits

@@
 %MRS: a molecular model can't really confirm or deny, because of the approximations.  provide evidence to support or call into question previous conclusions.
-will confirm or deny past drawn conclusions that have largely guided our understanding of separation mechanisms. 
+will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
 	\begin{itemize}
@@
                           %MRS: vvv this point has a partial answer as well as a question -- do you want that here?
+			  %BJC: This is meant to reference a paper where this calculation was done so it's technically past work
 			\item Does the equilibrated structure exist in distinct layers? Fourier analysis can help answer this question
@@
           %MRS: ``careful'': better to show, not tell that it is careful.
-		\item This paper will illustrate the careful development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
+		\item This paper will illustrate the development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
 		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
@@
                   %MRS: algorithm not really the main finding.
+		  %BJC: so don't mention it here then? maybe save it for the methods
 		\item We have written an algorithm to simulate the crosslinking mechanism and understand its influence on membrane structure
@@
 %MRS: justify choice of 20?
+%BJC: let's brainstorm the right way to justify	
 	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
@@
         %MRS: this probably isn't so important it should be a figure in the main paper (maybe supporting).
+	%BJC: I thought the same thing but just put it here temporarily
 	\includegraphics{placeholder.png}
@@
 %MRS: I though sandwitched not that stable?
+%BJC: It can stay stable, although there is an apparent shift away from perfect stacking with time. See results of measuring overlap
 		\item Sandwiched and parallel-displaced configurations are both stable for 100's of nanoseconds and give reasonable xray diffraction patterns.
@@
 		\item This will be called phase B (Fig~\ref{fig:phaseB})
-		\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be fit to a gaussian distribution % BJC: supplemental info probably %MRS: anything can be fit to.
+		\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution % BJC: supplemental info probably %MRS: anything can be fit to.
 Do you mean well-approximated by?
@@
 %MRS: probably should point out things that both models get right, like the C-C isotropic band.
+%BJC: added as an item
 	Comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration
@@
 %MRS: just wondering, are the offset configurations pi-stacking distances closer than the direct stacking ones?  Seem like might be.
+%BJC: They are the same. See journal entry from week of 4/21/2017
+			%BJC: New point vv
+			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, can be made to appear with an average tilt angle of 0 degrees
 		\end{itemize}
@@
 		\end{itemize}
+		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\texsuperscript{-1} which is typical of packed alkane chains
+		\item Both phases exhibit axial reflections.
+Even though the rings are not ordered in phase B, they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present
 	\end{itemize}
@@
 Or is this just notes for us?
+	%BJC: Sorry, meant this to be more along the lines of "Questions for us to answer before submitting this paper"
 	Questions to answer from here:
@@
 
-	The model gives reasonable estimates of ionic conductivity.
+	The model gives reasonable estimates of ionic conductivity for both phases.
 	\begin{itemize}
@@
 		\item See comparison of methods in Table~\ref{table:conductivity}
+		\item The ordered phase has a higher calculated ionic conductivity
 	\end{itemize}
@@
 	%MRS: seems like needs to be a bit more discussion about 5 vs 6 vs 7, and which is most likely? 
-        %MRS: will have to discuss a bit more about pi-stacking in GAFF and in reality, and how we might expect that will chage things.
+        %MRS: will have to discuss a bit more about pi-stacking in GAFF and in reality, and how we might expect that will change things.
 

### 2017-04-27 Ben_Manuscripts/Paper1/methods.tex
more text writtenx

@@
 continuity in all directions, avoiding any edge effects and creating an
-infinite length pore ideal for studying transport
-(Fig.~\ref{fig:initial}). A small number of layers is preferred in order
-to reduce computational cost and to allow us look at longer timescales.
-Ultimately, we chose to build a system with 20 layers of monomer in each
-pore in order to give sufficient resolution when simulating X-ray 
-diffraction patterns.
+infinite length pore ideal for studying transport. A small number of
+layers is preferred in order to reduce computational cost and to allow
+us look at longer timescales. Ultimately, we chose to build a system
+with 20 layers of monomer in each pore in order to give sufficient
+resolution when simulating X-ray diffraction patterns.
 
 % Questionably needed figure
-\begin{figure}
-\includegraphics{placeholder.png}
-	\caption{Monomers are placed in an initial configuration close to
-	         the expected equilibrium configuration and allowed to relax}
-	\label{fig:initial}
-\end{figure}
+%\begin{figure}
+%\includegraphics{placeholder.png}
+%	\caption{Monomers are placed in an initial configuration close to
+%	         the expected equilibrium configuration and allowed to relax}
+%	\label{fig:initial}
+%\end{figure}
 
@@
 equilibration, force constants are reduced by the square root of the 
-previous force constant, with a starting value of 1e6.  by the
+previous force constant every 50 ps, with a starting value of 1e6 kJ
+mol\textsuperscript{-1} nm\textsuperscript{-2}. Once the force constant
+is below 10 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}, the 
+restraints are slowly released until there is no more restriaining 
+potential. All restrained equilibrations are run in the NVT ensemeble. 
+The resulting unrestrained structure is subsequently allowed to 
+equilibrate in the NPT ensemble for > 200 ns.
+
+Determination of equilibration 
 \begin{itemize}
-	\item Equilibration scheme:
-	\begin{itemize}
-		\item Apply position restraints to monomer head groups during energy minimization 
-		\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
-		\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
-		\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate 
-	\end{itemize}
-\end{itemize}
+	\item Pore spacing 
+	\item Benzene ring stacking
+	\item
 
-Using an equilibrated structure, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
-\begin{itemize}
-	\item Crosslinking maintains alignment of cylindrical mesophases - emphasize that replicating the mechanism/kinetics is not important 
-	\item head to tail addition dominates so I only implemented that
-	\item racemic mixture - don't have to be too concerned about direction of attack 
-	\item Details of crosslinking algorithm (refer to appendix or supplemental info but give a brief overview here)
-\end{itemize}
+Using an equilibrated structure, a crosslinking procedure was performed
+in order to better parallel synthetic procedures. The purpose of 
+crosslinking is to maintain macroscopic alignment of the crystalline
+domains, ensuring aligned, hexagonally packed pores. For that reason, we
+are not concerned with replicating the kinetics of the reaction, but
+instead emphasize the consistency of the final structure with experimental
+structural data. The algorithm was developed based on the known reaction
+mechanism. Crosslinking of this system is a free radical polymerization (FRP)
+taking place between terminal alkyl groups present on each of the three
+monomer tails. FRPs require an initiator which bonds to the system, 
+meaning new atoms were introduced into the system. For simplicity, the 
+initiator was simulated as hydrogen and made present in the simulation
+by including them in all possible bonding positions as dummy atoms.
+The crosslinking procedure is carried out iteratively. During each 
+iteration, bonding carbon atoms are chosen based on a distance cut-off.
+The topology is updated with new bonds and dummy hydrogen atoms are 
+changed to appropriate hydrogen types. Head-to-tail addition was the
+only propagation mode considered due to its dominance in real systems.
+Direction of attack was not considered because the resultant mixture is
+racemic. The resulting crosslinked structure has an even distribution of
+crosslinks between monomer tails of the same monomer, monomers stacked on
+top of each other and monomers in other pores, including across periodic
+boundaries. The pore spacing shrinks by $\approx$ 1 nm and stays 
+constant under a range of simulation conditions (see supplemental info).
 
-Simulated X-ray diffraction patterns were generated based on atomic coordinates to give a deeper understanding of the pore structure and spacing. 
-\begin{itemize}
-	\item 3 dimensional fourier transformed electron density generates simulated 1D and 2D diffraction patterns
-        \item The 1D patterns are generated by spherical integration of the FT
-        \item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
-        \item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
-\end{itemize}
+Simulated X-ray diffraction patterns were generated based on atomic
+coordinates to give a deeper understanding of the pore structure and
+spacing. All atomic coordinates were simulated as gaussian spheres of
+electron density  corresponding to each atom's atomic number. A three
+dimensional fourier transform (FT) of the array of electron density 
+results in a 3 dimensional representation of the unit cell in reciprocal
+space. Cross sections of the 3D FFT result in two dimensional reciprocal
+space patterns which represent 2D diffraction patterns. Spherical
+integration of the FT yields a 1 dimensional curve which is the same
+as that generated in a diffraction experiment. We matched experimental
+1D and 2D WAXS patterns by iterative improvement of our choice of 
+initial structure and equilibration procedure
 

### 2017-05-02 Ben_Manuscripts/Outlines/Paper1_Outline.tex
updated outline

--- 2017-04-27 Ben_Manuscripts/Outlines/Paper1_Outline.tex
@@
 			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer 
-                          %MRS: vvv this point has a partial answer as well as a question -- do you want that here?
-			\item Does the equilibrated structure exist in distinct layers? Fourier analysis can help answer this question
 		\end{itemize}
@@
                   %MRS: algorithm not really the main finding.
-		\item We have written an algorithm to simulate the crosslinking mechanism and understand its influence on membrane structure
+		  %BJC: so don't mention it here then? maybe save it for the methods
+		\item We examined crosslinking mechanism and understand its influence on membrane structure
                   %MRS: the fact that we can is not that much interest, rather that we do.  Restate along lines of ``we havecompared simulated x-ray diffraction to experiment''
@@
 	\end{itemize}
-%MRS: justify choice of 20?	
+
 	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
@@
 		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
+                \item Decided on 20 layers using a system which held a vacuum gap above and below the membrane
+                \item Too few layers leads to micelle-like formations
 	\end{itemize}
@@
 	\begin{figure}
-          %MRS: this probably isn't so important it should be a figure in the main paper (maybe supporting).
+
 	\includegraphics{placeholder.png}
@@
 	% Ionic conductivity here probably
+	The Nernst Einstein relation and the Collective Diffusion model were both applied to the system in order to estimate ionic conductivity.
+		\item There are a few ways to estimate ionic conductivity as seen in literature.
+We prefer a method which can extract an estimate based purely on an equilibrium trajectory (reference to computational electrophysiology)
+                \item We must also be sure that our analysis of results is consistent with the method used for experimental evaluation (i.e. AC impedance spectroscopy)
+                \item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system. %BJC: worth getting into? Could also just say 
+		% that we expect our calculated value to be higher since ours is perfectly aligned relative to the real system.
+                \item Two methods used to for prediction
+                %BJC: probably belongs in methods:
+                \item Nernst Einstein Relation:
+                \begin{itemize}
+                        \item Widely used equation for estimating ionic conductivity
+                        \item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
+                        \item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
+                        \item Concentration is concentration of ions in the whole membrane, not just channels
+                \end{itemize}
+                \item Collective Diffusion:  %BJC: will have a very topical explanation followed by a reference to the paper from which I got the method
+                \begin{itemize}
+                        \item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
+                        \item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
+                        \item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
+                        \item A similar model has been derived and validate to predict water permeability using equilibrium simulations
+                        \item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores.
+One would expect single channel IC to be much larger than the bulk membrane
+                \end{itemize}
+        \end{itemize}
+
 	\section{Results and Discussion}
 
-	Varying number of monomers in each stacked layer between 4 and 8, as well as the benzene stacking configuration between sandwiched and parallel displaced, results in more than one stable structures.
+	In order to construct an initial configuration which gives reliable trends, we need to understand the composition of layers, how far apart to stack the layers, and how to orient them with respect to each other.
+
+	To understand the composition of the monomer layers, we ran simulations created with 4 - 8 monomers per layer 
 	\begin{itemize}
-                \item We did a systematic study of the properties resulting from each starting configuration
-		\item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. Pore spacing should be $\approx$ 4.1 nm
-		\item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Fig~\ref{table:p2p})  % I think even six is too big.
-Leaving it in consideration though since the disordered version gives pretty good p2p distances
+		\item All configurations were stable for at least a short time %BJC: I am going to run out these simulations further and will have more to say
+                \item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Fig~\ref{table:p2p})
+        \end{itemize}
+
+        The initial distance between layers is a key determining factor of the equilibrium configuration.
+	\begin{itemize}
+                \item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. 
                 \item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure.
@@
 Also, maybe include thickness in the table?
-		\item This will be called phase A for simplicity  % BJC: I can come up with better phase names if that's important
-%MRS: I though sandwitched not that stable?
-		\item Sandwiched and parallel-displaced configurations are both stable for 100's of nanoseconds and give reasonable xray diffraction patterns.
-		\item hypothesis: Parallel displaced is more stable and allows the benzene rings to stack closer together  
-	\end{itemize}
-
-	%\begin{wraptable}{m}{5.5cm}
-	\begin{table}
-	\centering
-	\begin{tabular}{|c|c|}
-	\hline
-	table & here \\
-	\hline
-	\end{tabular}
-	\caption{Pore spacings inconsistent with experimentally measured data indicate that the respective configuration will%MRS: maybe not be the most stable? 
-not be stable in a laboratory setting and should not be studied further~\label{table:p2p}}  
-	\end{table}
-	%\end{wraptable}
-
-	%BJC: Simulations of systems built by stacking monomers in the parallel-displaced and stacked configurations results in two different structures that are both stable for $>$ 500 ns, suggesting the existence of more than one metastable state.
+                \item This will be called phase A for simplicity  
 	        Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
@@
                 	\item This will be called phase B (Fig~\ref{fig:phaseB})
-		\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be fit to a gaussian distribution % BJC: supplemental info probably %MRS: anything can be fit to.
-Do you mean well-approximated by?
+                	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
                 	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the starting configuration
@@
         \end{itemize}
+
+	We varied the relative interlayer orientation between sandwiched and parallel-displaced based on our knowledge of the stability of these two pi-stacking modes.
+        \begin{itemize}
+		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a clear relation between the parallel displaced and sandwiched configuration %BJC: A figure would probably be good here
+		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
+		\item Both configurations are stable for 100's of nanoseconds
+		\item Xray diffraction of the sandwiched configuration after equilibration shows the spots. This indicates that there is a shift towards the offset configuration.
+	\end{itemize}
+
+	The stability of crystalline phases is strongly dependent on temperature, requiring evaluation of our force field's ability to represent the temperature at which we are simulating.
+	\begin{itemize}
+		\item All of the above simulations were ran at 280K and 300K
+		\item Phase A is very stable at 280K
+		\item when bumped to 300K it is also stable, however with a larger degree of disorder %BJC: can quantify this with order parameter
+		\item We see a clear transition to Phase B for any starting configuration when the temperature is raised above 310K (~\ref{fig:transition})
+		\item Simulating the system at room temperature should be sufficient to see both phases
+	\end{itemize}
+
+	A summary of all experiments and relevant structural parameters are presented in table ~\ref{fig:p2p}
+
+	\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{placeholder.png}
+	\caption{As temperature is increased, Phase A transitions to Phase B, as indicated by the shown order parameter.
+An order parameter of 1 indicates perfect ordering, while 0 indicates disorder~\label{fig:transition}}
+	\end{figure}
+
+	\begin{table}
+	\centering
+	\begin{tabular}{|c|c|}
+	\hline
+	table & here \\
+	\hline
+	\end{tabular}
+	\caption{The system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data~\label{fig:p2p} 
+	\end{table}
 
@@
 	\end{subfigure}
-	\caption{Different pore structure are clear between systems built with benzene rings stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
+	\caption{There are clear differences in pore structure between systems built with layers stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
 	\label{fig:porestructures}
 	\end{figure}
-%MRS: probably should point out things that both models get right, like the C-C isotropic band.
+
 	Comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration
@@
 			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
-%MRS: just wondering, are the offset configurations pi-stacking distances closer than the direct stacking ones?  Seem like might be.
+			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
 		\end{itemize}
@@
         \end{subfigure}
-	\caption{Phase A (a) provides a good match to experiment (b). Phase B (c) is missing reflections present in the experimental pattern}
+	\caption{Phase A (a) provides a good match to experiment (b). Phase B (c) is missing reflections present in the experimental pattern} % BJC: any more detail? 
 	\label{fig:xrd}
@@
 
-	%BJC: generated 1D SAXS somewhere?? Just to show that we get the spacing right
-        %MRS: reasonable estimates for which structure?
-	The model gives reasonable estimates of ionic conductivity.
+	The model gives reasonable estimates of ionic conductivity for both phases.
 	\begin{itemize}
-		\item There are a few ways to estimate ionic conductivity as seen in literature. We prefer a method which can extract an estimate based purely on an equilibrium trajectory
-		\item We must also be sure that our analysis of results is consistent with the method use for experimental evaluation (i.e. AC impedance spectroscopy)
-		\item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system. %BJC: worth getting into? See comment below.
-		%BJC: We should discuss how we will actually make the link.
-We talked about it once but kind of left it hanging.
-It will likely be just some constant that we multiply our number by.
-To calculate the constant, I think using the azimuthal distribution is a good way to go about it.
-Although for that we'd need more data points telling us ionic conductivity as a function of azimuthal angle.
-That data will definitely be hard to come by in the near future so maybe a linear model is an okay estimate for now -- just to have something.
-For that, we know ionic conductivity with randomly oriented crystalline domains and we know ionic conductivity of a 'perfectly' aligned system (from our simulations).
-So we can make ionic conductivity as a linear function of alignment, I(x) (Actually it'd be piecewise with opposite slopes on either side of the an azimuthal angle of 90).
-Then we can integrate the azimuthal distribution weighted by I(x) to get a number to multiply our measurements by.
-		\item Two methods used to for prediction
-		%BJC: probably belongs in methods:
-		\item Nernst Einstein Relation:
-		\begin{itemize}
-			\item Widely used equation for estimating ionic conductivity
-			\item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
-			\item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
-			\item Concentration is concentration of ions in the whole membrane, not just channels
-		\end{itemize}
-		\item Collective Diffusion:  %BJC: will leave explanation of how I did it for supplemental info (so most of the following). Will just reference paper
-		\begin{itemize}
-			\item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
-			\item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
-			\item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
-			\item A similar model has been derived and validate to predict water permeability using equilibrium simulations
-			\item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores.
-One would expect single channel IC to be much larger than the bulk membrane
-		\end{itemize}                    
 		\item See comparison of methods in Table~\ref{table:conductivity}
+		\item The methods agree reasonably well within error
+		\item In the future, we will probably only use Nernst Einstein because it requires less simulation to get good statistics. %BJC: probably don't need to mention this
+		\item Our calculated values are higher than experimental values, as expected.
+		\item The real system, although mostly aligned and straight, still has a distribution of azimuthal angles, lowering the effective ionic conductivity of the bulk membrane. 
+		\item The ordering from isotropic to mostly aligned mesophases showed an 85x increase in ionic conductivity. We would expect more gains in a perfect system.
+		\item The ordered phase has a higher calculated ionic conductivity than the disordered phase.
 	\end{itemize}
@@
 	\end{tabular}
-	\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error~\label{table:conductivity}}
+	\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error.
+Both methods give calculated values of ionic conductivity which are higher than experimental values~\label{table:conductivity}}
 	\end{table}
@@
 Using the design framework and analysis methods applied herin, we have the ability to reliably predict structures of new nanoporous membranes.
-
-	%MRS: seems like needs to be a bit more discussion about 5 vs 6 vs 7, and which is most likely? 
-        %MRS: will have to discuss a bit more about pi-stacking in GAFF and in reality, and how we might expect that will chage things.
 
@@
 		\item The model's physical properties are consistent with experimental measurements
-		\item Channels are more disordered than previously thought and are filled with organic matter rather than hollow 
-                  %MRS: vvvv this is true even for parallel displaced?
-		\item There are likely no defined layers
-		\item Results presented for Colh phase monomer but methods are readily adapted to other LCs
+		\item We have discovered the existence of two metastable configurations that persist at room temperature
+		\item This methodology has been developed for a specific case but can be readily adapted to other LLCs
 	\end{itemize}
+	% focus around what we learned about the system - not that we have a model
 
@@
 
+        \includegraphics{placeholder.png}
+                \caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
+                \label{fig:initial}
+        \end{figure}
+
 	\noindent Crosslinking details

### 2017-05-02 Ben_Manuscripts/Paper1/methods.tex
updated outline

@@
 
-HII monomers were parameterized using the Generalized Amber Forcefield
-with the Antechamber package provided with AmberTools16. Charges were
-assigned using tools from Openeye Scientific Software. All molecular dynamics
-simulations were run using Gromacs version 5.1.2 and Gromacs version 2016.
+HII monomers were parameterized using the Generalized AMBER Forcefield
+\cite{wang_development_2004} with the Antechamber package\cite{wang_automatic_2006}
+provided with AmberTools16\cite{case_ambertools16_2016}. Charges were
+assigned using tools from Openeye Scientific Software. All molecular 
+dynamics simulations were run using Gromacs version 5.1.2 and Gromacs 
+version 2016. \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,
+van_der_spoel_gromacs:_2005,hess_gromacs_2008}
 
@@
 charges, the monomer system was annealed again and multiple monomer
-configurations were pulled from the trajectory.
+configurations were pulled from the trajectory to be used for full
+system construction.
 
@@
 Previous work has shown a coarse grain model self assemble into the HII
-phase configuration in $\approx$ 1000 ns. Atomistic self-assembly was 
-attempted by packing monomers into a box using Packmol. Simulations of >
-100 ns show no progress towards an ordered system. To bypass the 
-slow self-assembly process, python code was written in order that 
-assembles monomers into a configuration close to the expected 
-equilibrium configuration. A short, restrained equilibration, followed 
-by NPT simulations > 500 ns, allows the initial configuration to relax
-into an equilibrium configuration.
+phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
+Atomistic self-assembly was attempted by packing monomers into a box 
+using Packmol\cite{martinez_packmol:_2009}. Simulations of $>$ 100 ns 
+show no progress towards an ordered system. To bypass the slow self-assembly
+process, python code was written that assembles monomers into a structure 
+close to the expected equilibrium configuration. A short, restrained 
+equilibration, followed by NPT simulations $>$ 500 ns, allows the initial
+configuration to relax into an equilibrium configuration. Our logic for
+choosing a starting configuration and the details of the equilibration 
+schemes are presented below.
 
@@
 development. The distance between pores was based on experimental SAXS
-data for this system. Initial configuration pore spacing was chosen to
-be 10 \% larger than the experimental value. The layer spacing was based
-on reflections from experimental WAXS data at 3.7 \angstrom, thought to
-represent pi-stacking between stacked benzene rings. The tendency of 
-simulations to equilibrate to slightly larger interlayer spacing 
-inspired systems starting with layer spacings > 4 \angstrom.
+data for this system \cite{feng_thin_2016}. Initial configuration pore
+spacing was chosen to be 10 \% larger than the experimental value. 
+The layer spacing was based on reflections from experimental 2D WAXS
+data at 3.7 \angstrom, thought to represent pi-stacking between stacked
+benzene rings\cite{feng_scalable_2014}. The tendency of simulations to
+equilibrate to slightly larger interlayer spacing inspired systems
+starting with layer spacings $>$ 4 \angstrom.
 % There is plenty I can say about initial configuration. Starting layers
@@
 as a variable. Initial pore radius estimates were based on past TEM 
-images and size exclusion rejection data.
+images and size exclusion rejection data\cite{feng_scalable_2014,
+feng_thin_2016,zhou_supported_2005}.
 
@@
 prevents unrealistic jumps during early equilibration steps. Restraints
-allow the system to remain in the sandwiched and parallel-displaced 
+allow the monomer head groups to remain in the sandwiched or parallel-displaced 
 configurations while monomer tails settle. Doing so also helps prevent
@@
 equilibration, force constants are reduced by the square root of the 
-previous force constant every 50 ps, with a starting value of 1e6 kJ
+previous force constant every 50 ps, with a starting value of 1e6 KJ
 mol\textsuperscript{-1} nm\textsuperscript{-2}. Once the force constant
@@
 restraints are slowly released until there is no more restriaining 
-potential. All restrained equilibrations are run in the NVT ensemeble. 
+potential. All restrained equilibrations are run in the NVT ensemble. 
 The resulting unrestrained structure is subsequently allowed to 
-equilibrate in the NPT ensemble for > 200 ns.
+equilibrate in the NPT ensemble for $>$ 200 ns.
 
-Determination of equilibration 
-\begin{itemize}
-	\item Pore spacing 
-	\item Benzene ring stacking
-	\item
+%Determination of equilibration 
+%\begin{itemize}
+%	\item Pore spacing 
+%	\item Benzene ring stacking
+%\end{itemize}
 
@@
 mechanism. Crosslinking of this system is a free radical polymerization (FRP)
-taking place between terminal alkyl groups present on each of the three
+taking place between terminal vinyl groups present on each of the three
 monomer tails. FRPs require an initiator which bonds to the system, 
@@
 top of each other and monomers in other pores, including across periodic
-boundaries. The pore spacing shrinks by $\approx$ 1 nm and stays 
+boundaries. The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
 constant under a range of simulation conditions (see supplemental info).
@@
 results in a 3 dimensional representation of the unit cell in reciprocal
-space. Cross sections of the 3D FFT result in two dimensional reciprocal
+space. Cross sections of the 3D FT result in two dimensional reciprocal
 space patterns which represent 2D diffraction patterns. Spherical
@@
 
-% Ionic conductivity here probably
+Ionic conductivity was calculated using two different methods for
+robustness. The Nernst-Einstein relation relates 
+the DC ionic conductivity to ion diffusivity, $D$, concentration,
+$C$, ion charge, $q$, the boltzmann constant, $k_b$, and temperature,
+$T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$ Sodium ion diffusion 
+coefficients were found by calculating the slope of mean square
+displacement curve as indicated by the einstein relation
+\cite{einstein_investigations_1956}. Ion concentration was measured with
+respect to the entire unit cell. The second method, termed the 'Collective
+Diffusion' model \cite{liu_collective_2013}, measures the movement of
+the collective variable, Q, which is defined as the amount of charge 
+transfer through the system. The diffusion coefficient of Q, $D_Q$, can
+be calculated using the einstein relation. The conductance, $\gamma$ of
+the system can be calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$ 
+Conversion to ionic conductivity is achieved by multiplying by channel 
+length and dividing by the membrane cross sectional area. A full 
+derivation of the model can be accessed elsewhere\cite{liu_collective_2013}.

### 2017-05-02 Ben_Manuscripts/Outlines/Paper1_Outline.tex
edits

@@
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
-%MRS: we probably will want to add in Glaser's student (and possibly glaser) for their work on the X-ray simulations.
-%MRS: also possibly Xunda if we end up using X-ray diffraction images of theirs that are not published.
+\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joseph Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
 \begin{document}
@@
                 %MRS: Doug should have information on the chemistry here and how resistant they might be.
+		%BJC: Doug said they didn't do any chemical stability testing since the membranes had flux problems in the first place. So I won't mention this
 		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
@@
                 \begin{itemize}
+                        \item What does the microscopic pore structure look like?
 			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
-                          %MRS: vvv this point below should be made more specific.  Ionic gradient at the end?  Donnan exclusion?
-                        \item Does concentration of ions in the pore repel incoming ions?
+			\item Is rejection of ions due to donnan exclusion?
                         \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
-                         %MRS: vvv can you be a bit more specific about ``transport barriers?''
-                        \item Is water structured inside the pores leading to transport barriers?
-                          %MRS: vvv maybe put this higher, since the other bullet points above are dependent on this.
-Also, this point conflacts understanding the structure, and then modifying it, which are sort of two steps.
-			\item What does the microscopic pore structure look like and how can we relate that to monomer design and transport?
+                        \item Is water structured inside the pores, restricting low energy pathways for solutes to follow? %BJC: saw something like this in a paper
 		\end{itemize}
+		\item How can microscopic pore structure guide membrane design
 		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
@@
 
-	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, 
-%MRS: a molecular model can't really confirm or deny, because of the approximations.  provide evidence to support or call into question previous conclusions.
-will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
+	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms.
 	\begin{itemize}
@@
 			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
-			\item Substituted benzene preferred stacking mode? Learning more about this   	
+			\item Substituted benzene rings exhibit an even stronger pi-stacking attraction %BJC: reference ab initio papers   	
 			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
-			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer 
+			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer % reference 2005-ish Zhou paper 
 		\end{itemize}
@@
 	\begin{itemize}
-          %MRS: ``careful'': better to show, not tell that it is careful.
 		\item This paper will illustrate the development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
@@
 		\item We are primarily interested in reproducing the conclusions about structure which have been made from XRD experiments and ionic conductivity measurements.    
-                  %MRS: algorithm not really the main finding.
-		  %BJC: so don't mention it here then? maybe save it for the methods
+		\item We have comparied simulated X-ray diffraction patterns to experiment in order to match major features present in the 2D patterns
+		\item We can predict ionic conductivity using two agreeing methods -- Collective diffusion and nernst einstein
 		\item We examined crosslinking mechanism and understand its influence on membrane structure
-                  %MRS: the fact that we can is not that much interest, rather that we do.  Restate along lines of ``we havecompared simulated x-ray diffraction to experiment''
-		\item We can simulate x ray diffraction patterns based on atomic coordinates in order to compare major features present in the 2D patterns
-		\item We can predict ionic conductivity using two agreeing methods -- Collective diffusion and nernst einstein
 	\end{itemize}
@@
 		\item Antechamber used for atomtyping with gaff forcefield
-		\item Used Openeye Quacpac molcharge.py to assign charges %MRS: explain reason for 2 charge steps.
+		\item Used Openeye Quacpac molcharge.py to assign charges
+		\item The am1bccsym method provided with Quacpac performs a conformational search and applies charges symmetrically based on the lowest energy subset of possible conformations
 		\item Anneal again 
-		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
-		\item Manual modifications to the structure were made to create specific geometries for xray diffraction experiments
+		\item Multiple configurations saved from annealing trajectory to prove independence of starting config. A representative structure is given in Figure ~\ref{fig:monatomistic}
+		\item Manual modifications to the structure were made to create specific geometries for X-ray diffraction experiments
 	\end{itemize}
+
+	%BJC: I'm not sure where to place this figure. ACS nano requires the methods section to go last (after conclusions). It seems like this should go earlier, but it fits the context best around here.
+	\begin{figure}
+	\centering
+	\begin{subfigure}{.45\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{}\label{fig:chemdraw}
+	\end{subfigure}
+	\begin{subfigure}{.45\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{}\label{fig:monatomistic}
+	\end{subfigure}
+	\medskip
+	\begin{subfigure}{.45\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{}\label{fig:cartoonlayer}
+	\end{subfigure}
+	\begin{subfigure}{.45\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{}\label{fig:layeratomistic}
+	\end{subfigure}
+	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition about system behavior (c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests geometric constraints based on monomer structure}\label{fig:cartoonvatomistic}
+	\end{figure}
 
@@
 		\begin{itemize}
-			\item Packed monomers into box
+			\item Packed monomers into box with Packmol
 			\item Simulated for ~100 ns with no progress shown towards self assembly
@@
 	\end{itemize}
-
-	\begin{figure}
-
-	\includegraphics{placeholder.png}
-		\caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
-		\label{fig:initial}
-	\end{figure}
 
@@
 			\item Apply position restraints to monomer head groups during energy minimization 
-			\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
+			\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting monomer configuration)
 			\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
@@
 
-	% Ionic conductivity here probably
 	The Nernst Einstein relation and the Collective Diffusion model were both applied to the system in order to estimate ionic conductivity.
+	\begin{itemize}
 		\item There are a few ways to estimate ionic conductivity as seen in literature.
@@
                 \item Two methods used to for prediction
-                %BJC: probably belongs in methods:
                 \item Nernst Einstein Relation:
@@
 		\item All configurations were stable for at least a short time %BJC: I am going to run out these simulations further and will have more to say
-                \item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Fig~\ref{table:p2p})
+                \item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Table~\ref{table:p2p})
         \end{itemize}
@@
                 \item This will be called phase A for simplicity  
-	        Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
+	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
         	\begin{itemize}
@@
                 	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
-                	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the starting configuration
+                	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the initial interlayer spacing
                 	\item The phase is also present when phase A is heated close to its isotropic transition point
@@
                 	\end{itemize}
+		\end{itemize}
                 \item We have at least two metastable states
@@
         \begin{itemize}
-		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a clear relation between the parallel displaced and sandwiched configuration %BJC: A figure would probably be good here
+		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a clear relation between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here
 		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
-		\item Both configurations are stable for 100's of nanoseconds
+		\item However, both configurations are stable for 100's of nanoseconds
 		\item Xray diffraction of the sandwiched configuration after equilibration shows the spots. This indicates that there is a shift towards the offset configuration.
@@
 
-	A summary of all experiments and relevant structural parameters are presented in table ~\ref{fig:p2p}
+	A summary of all experiments and relevant structural parameters are presented in table ~\ref{table:p2p}
 
@@
 	\caption{As temperature is increased, Phase A transitions to Phase B, as indicated by the shown order parameter.
-An order parameter of 1 indicates perfect ordering, while 0 indicates disorder~\label{fig:transition}}
+An order parameter of 1 indicates perfect ordering, while 0 indicates disorder}\label{fig:transition}
 	\end{figure}
@@
 	\end{tabular}
-	\caption{The system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data~\label{fig:p2p} 
+	\caption{A system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data}\label{table:p2p} 
 	\end{table}
@@
 
-	Comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration
+	%BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
+	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
 	\begin{itemize}
@@
 		\end{itemize}
-		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\texsuperscript{-1} which is typical of packed alkane chains
+		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\textsuperscript{-1} which is typical of packed alkane chains
 		\item Both phases exhibit axial reflections.
@@
 		\item Pore-to-pore equilibration plots
-                  %MRS: ^^^ probably should include how we determined if we ran long enough.
+		\item Plots of other things that level off indicating equilibration
 		\item 3D visualizations of different configurations tested
-                  %MRS: vvv this might be in the main text, since it is what allows us to say what is more likely.
-		\item Table of measurements on 5-8 monomer per layer configurations
 		\item Sodium ion distribution in disordered phase
@@
 
+        \begin{figure}
+		\centering
 		\includegraphics{placeholder.png}

### 2017-05-03 Ben_Manuscripts/Outlines/Paper1_Outline.tex
more edits

@@
 	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale allowing design of solute-specific separation membranes.
+
+	While RO anad NF have seen many advances in the past few decades, they are far from perfect separation technologies
 	\begin{itemize}
@@
 		%BJC: Doug said they didn't do any chemical stability testing since the membranes had flux problems in the first place. So I won't mention this
+		\item nanofiltration was introduced as an intermediate between RO and ultrafiltration
+		\item Larger and well-defined pores drive down energy requirements while still affording separation of solutes as small as ions, to some degree
+		\item Like RO membranes, NF membranes have a pore size distribution which limits their ability to perform precise separations
+	\end{itemize}
+
+	Nanostructured membranes can bypass many of the performance issues which plague traditional NF and RO membranes.
+	\begin{itemize}
 		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
@@
 			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
-			%BJC: The following are ideas pulled from the grant. I need to do some reserach and come up with some one liners as to why each have not been successful
-			\item Track-etch membranes
-		    	\item Molecular squares
-			\item Macrocyclic surfactants 
+			\item Zeolites - sub-nm pores with good MD results but interstitial defects created during manufacturing kill selectivity 
 		\end{itemize}

### 2017-05-03 Ben_Manuscripts/Paper1/intro.tex
Writing it up

--- 2017-05-02 Ben_Manuscripts/Outlines/Paper1_Outline.tex
@@
-\documentclass{article}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{geometry}
-\geometry{legalpaper, margin=1in}
-\usepackage{amsmath} % or simply amstext
-\newcommand{\angstrom}{\textup{\AA}}
-\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joseph Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
-\begin{document}
-	\bibliographystyle{ieeetr}
-	\graphicspath{{./figures/}}
-	\maketitle
-	\section{Introduction}
-	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale allowing design of solute-specific separation membranes.
-	\begin{itemize}
-		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
-		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
-		\item Designing RO membranes to achieve targeted separations of specific solutes is nearly impossible due to the separation (hypothesized to be) controlled by fluctuating polymer voids
-		\item RO has difficulty separating neutral organics because they tend to dissolve in polymer matrix
-		\item Many current RO membranes degrade in typical chlorine filled municipal water supplies (debating this point because there aren't any studies of LLC membrane fouling resistance)
-                %MRS: Doug should have information on the chemistry here and how resistant they might be.
-		%BJC: Doug said they didn't do any chemical stability testing since the membranes had flux problems in the first place. So I won't mention this
-		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
-		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
-		\item Entirely different mechanisms govern the separation processes in various nanostructured materials which can inspire novel separation techniques
-	\end{itemize}
+\section*{Introduction}
 
-	Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
-	\begin{itemize}
-		\item Leading technologies and their limitations:
-		\begin{itemize}
-			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact selectivity
-			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
-			%BJC: The following are ideas pulled from the grant. I need to do some reserach and come up with some one liners as to why each have not been successful
-			\item Track-etch membranes
-		    	\item Molecular squares
-			\item Macrocyclic surfactants 
-		\end{itemize}
-	\end{itemize}
+Nanostructured membrane materials have become increasingly popular for 
+aqueous separations applications because they offer the ability to 
+control membrane architecture at the atomic scale allowing design of 
+solute-specific separation membranes \cite{humplik_nanostructured_2011}.
+Most membrane-based aqueous separations of small molecules can be 
+achieved using reverse osmosis (RO) or nanofiltration (NF).
 
-	Self assembling lyotropic liquid crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques feasible for large scale production.
+While RO and NF have seen many advances in the past few decades, they 
+are far from perfect separation technologies. Current state-of-the-art
+RO membranes are unstructured with tortuous and polydisperse diffusion
+pathways which can lead to inconsistent performance. Tortuosity and 
+polydispersity drive up energy requirements which strain developing regions and 
+contribute strongly to CO\textsubscript{2} emissions. Designing RO 
+membranes to achieve targeted separations of specific solutes is nearly
+impossible. Various solutes dissolve into and diffuse through the polymer
+matrix at different rates. At best, one can exploit these differences 
+to create a functional selective barrier. NF was introduced as an 
+intermediate between RO and ultrafiltration (UF), having the abilitiy to
+separate organic matter and salts on the order of one nanometer in size.
+Larger and well-defined pores drive down energy requirements while still
+affording separation of solutes as small as ions to some degree. This is
+why NF is often used as a precursor to reverse osmosis. Unfortunately,
+NF membranes, like RO, are produced with a pore size distribution which 
+limits their ability to perform precise separations.
+
+Nanostructured membranes can bypass many of the performance issues which
+plague traditional NF and RO membranes. Targeted separations can be 
+accomplished by tuning size and functionality of the molecular building
+blocks which form these materials. Solute rejecting pore sizes can be
+tuned uniformly, resulting in sharp size cut-offs. Entirely different
+mechanisms may govern the separation processes in a given nanostructured
+material which can inspire novel separation techniques.
+
+Development of nanostructured materials has been limited by the ability
+to synthesize and scale various fundamentally sound technologies.
+Graphene sheets are atomically thick which gives excellent permeability
+but defects during manufacturing severely impact selectivity 
+\cite{cohen-tanugi_multilayer_2016}. Molecular dynamics simulations of
+carbon nanotubes show promise \cite{humplik_nanostructured_2011} but 
+synthetic techniques are unable to achieve scalable alignment and pore
+monodispersity \cite{hata_water-assisted_2004,maruyama_growth_2005}.
+Zeolites have sub-nm pores with a narrow size distribution and MD simulations
+exhibited complete rejection of solvated ions \cite{murad_molecular_1998},
+however, experimental rejection was low and attributed to interstitial
+defects formed during membrane synthesis \cite{li_desalination_2004}.
+
+Self assembling lyotropic liquid crystals (LLCs) share the characteristic
+ability of nanostructured membrane materials to create highly ordered 
+structures with the added benefits of low cost and synthetic techniques
+feasible for large scale production.
 \begin{itemize}
@@
 \end{itemize}
-
-	\section{Methods}
-
-	HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16.
-All molecular dynamics simulations were run using Gromacs version 5.1.2 and Gromacs version 2016.
-
-	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
-	\begin{itemize}
-		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
-		\item Result not global minimum but close enough for structure building
-		\item Antechamber used for atomtyping with gaff forcefield
-		\item Used Openeye Quacpac molcharge.py to assign charges
-		\item The am1bccsym method provided with Quacpac performs a conformational search and applies charges symmetrically based on the lowest energy subset of possible conformations
-		\item Anneal again 
-		\item Multiple configurations saved from annealing trajectory to prove independence of starting config. A representative structure is given in Figure ~\ref{fig:monatomistic}
-		\item Manual modifications to the structure were made to create specific geometries for X-ray diffraction experiments
-	\end{itemize}
-
-	%BJC: I'm not sure where to place this figure. ACS nano requires the methods section to go last (after conclusions). It seems like this should go earlier, but it fits the context best around here.
-	\begin{figure}
-	\centering
-	\begin{subfigure}{.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:chemdraw}
-	\end{subfigure}
-	\begin{subfigure}{.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:monatomistic}
-	\end{subfigure}
-	\medskip
-	\begin{subfigure}{.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:cartoonlayer}
-	\end{subfigure}
-	\begin{subfigure}{.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:layeratomistic}
-	\end{subfigure}
-	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition about system behavior (c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests geometric constraints based on monomer structure}\label{fig:cartoonvatomistic}
-	\end{figure}
-
-	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for a more efficient way to build the system.
-	\begin{itemize}
-		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
-		\item Attempts with Colh system not fruitful  
-		\begin{itemize}
-			\item Packed monomers into box with Packmol
-			\item Simulated for ~100 ns with no progress shown towards self assembly
-		\end{itemize}  
-		\item Wrote code to assemble monomers into Colh configuration close to what is expected 
-		\item Equilibration simulations allow structure to relax into expected configuration 
-	\end{itemize}
-
-	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
-	\begin{itemize}
-		\item A thinner system is better to reduce the computational cost and allow us to look at longer timescales
-		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
-                \item Decided on 20 layers using a system which held a vacuum gap above and below the membrane
-                \item Too few layers leads to micelle-like formations
-	\end{itemize}
-
-	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
-	\begin{itemize}
-		\item XRD gives Pore-to-Pore distances of $\approx$ 4.1 nm and indicates possible pi-stacking at $\approx$ 3.7 \angstrom (see figure~\ref{fig:xrd}) on - comparison of experimental vs. simulated)
-		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
-		\item T-shaped and parallel-displaced are nearly isoenergetic and more stable than the sandwiched configuration.
-		\item T-shaped configuration is most stable when benzene centers are $\approx$ 5 \angstrom apart which is not consistent with WAXS. % http://www.jbc.org/content/273/25/15458.full 
-		\item System made with stacked and parallel-displaced benzene rings to see what is favored and matches XRD
-		\item TEM images and rejection studies give a pore size estimate
-	\end{itemize}
-
-	An equilibration scheme with position restraints placed on benzene rings prevents unrealistic jumps during early equilibration steps.
-	\begin{itemize}
-		\item Equilibration scheme:
-		\begin{itemize}
-			\item Apply position restraints to monomer head groups during energy minimization 
-			\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting monomer configuration)
-			\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
-			\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate 
-		\end{itemize}
-	\end{itemize}
-
-	Using an equilibrated structure, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
-	\begin{itemize}
-		\item Crosslinking maintains alignment of cylindrical mesophases - emphasize that replicating the mechanism/kinetics is not important 
-		\item head to tail addition dominates so I only implemented that
-		\item racemic mixture - don't have to be too concerned about direction of attack 
-		\item Details of crosslinking algorithm (refer to appendix or supplemental info but give a brief overview here)
-	\end{itemize}
-
-	Simulated X-ray diffraction patterns were generated based on atomic coordinates to give a deeper understanding of the pore structure and spacing. 
-        \begin{itemize}
-               \item 3 dimensional fourier transformed electron density generates simulated 1D and 2D diffraction patterns
-               \item The 1D patterns are generated by spherical integration of the FT
-               \item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
-               \item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
-        \end{itemize}
-
-	The Nernst Einstein relation and the Collective Diffusion model were both applied to the system in order to estimate ionic conductivity.
-	\begin{itemize}
-		\item There are a few ways to estimate ionic conductivity as seen in literature.
-We prefer a method which can extract an estimate based purely on an equilibrium trajectory (reference to computational electrophysiology)
-                \item We must also be sure that our analysis of results is consistent with the method used for experimental evaluation (i.e. AC impedance spectroscopy)
-                \item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system. %BJC: worth getting into? Could also just say 
-		% that we expect our calculated value to be higher since ours is perfectly aligned relative to the real system.
-                \item Two methods used to for prediction
-                \item Nernst Einstein Relation:
-                \begin{itemize}
-                        \item Widely used equation for estimating ionic conductivity
-                        \item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
-                        \item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
-                        \item Concentration is concentration of ions in the whole membrane, not just channels
-                \end{itemize}
-                \item Collective Diffusion:  %BJC: will have a very topical explanation followed by a reference to the paper from which I got the method
-                \begin{itemize}
-                        \item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
-                        \item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
-                        \item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
-                        \item A similar model has been derived and validate to predict water permeability using equilibrium simulations
-                        \item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores.
-One would expect single channel IC to be much larger than the bulk membrane
-                \end{itemize}
-        \end{itemize}
-
-	\section{Results and Discussion}
-
-	In order to construct an initial configuration which gives reliable trends, we need to understand the composition of layers, how far apart to stack the layers, and how to orient them with respect to each other.
-
-	To understand the composition of the monomer layers, we ran simulations created with 4 - 8 monomers per layer 
-	\begin{itemize}
-		\item All configurations were stable for at least a short time %BJC: I am going to run out these simulations further and will have more to say
-                \item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Table~\ref{table:p2p})
-        \end{itemize}
-
-	The initial distance between layers is a key determining factor of the equilibrium configuration.
-	\begin{itemize}
-                \item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. 
-                \item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure.
-Benzene rings arrange in a helical conformation after equil.
-Membrane about 8 nm thick (Fig ~\ref{fig:phaseA}) % BJC: Still trying to prove that layered is trying to go towards a helical conformation.
-Also, maybe include thickness in the table?
-                \item This will be called phase A for simplicity  
-	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
-        	\begin{itemize}
-                	\item This will be called phase B (Fig~\ref{fig:phaseB})
-                	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
-                	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the initial interlayer spacing
-                	\item The phase is also present when phase A is heated close to its isotropic transition point
-                	\item There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
-                	\begin{itemize}
-                        	\item Phase B has a closed pore, while phase A is open. This will impact transport mechanisms
-                        	\item Phase B membranes are thicker
-                        	\item Consequently, the pore spacing is smaller
-                	\end{itemize}
-		\end{itemize}
-                \item We have at least two metastable states
-        \end{itemize}
-
-	We varied the relative interlayer orientation between sandwiched and parallel-displaced based on our knowledge of the stability of these two pi-stacking modes.
-        \begin{itemize}
-		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a clear relation between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here
-		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
-		\item However, both configurations are stable for 100's of nanoseconds
-		\item Xray diffraction of the sandwiched configuration after equilibration shows the spots. This indicates that there is a shift towards the offset configuration.
-	\end{itemize}
-
-	The stability of crystalline phases is strongly dependent on temperature, requiring evaluation of our force field's ability to represent the temperature at which we are simulating.
-	\begin{itemize}
-		\item All of the above simulations were ran at 280K and 300K
-		\item Phase A is very stable at 280K
-		\item when bumped to 300K it is also stable, however with a larger degree of disorder %BJC: can quantify this with order parameter
-		\item We see a clear transition to Phase B for any starting configuration when the temperature is raised above 310K (~\ref{fig:transition})
-		\item Simulating the system at room temperature should be sufficient to see both phases
-	\end{itemize}
-
-	A summary of all experiments and relevant structural parameters are presented in table ~\ref{table:p2p}
-
-	\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{placeholder.png}
-	\caption{As temperature is increased, Phase A transitions to Phase B, as indicated by the shown order parameter.
-An order parameter of 1 indicates perfect ordering, while 0 indicates disorder}\label{fig:transition}
-	\end{figure}
-
-	\begin{table}
-	\centering
-	\begin{tabular}{|c|c|}
-	\hline
-	table & here \\
-	\hline
-	\end{tabular}
-	\caption{A system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data}\label{table:p2p} 
-	\end{table}
-
-	\begin{figure}
-	\centering
-	\begin{subfigure}{.45\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:phaseA}}
-	\end{subfigure}
-	\begin{subfigure}{.45\textwidth}
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\centering
-		\caption{~\label{fig:phaseB}}
-	\end{subfigure}
-	\caption{There are clear differences in pore structure between systems built with layers stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
-	\label{fig:porestructures}
-	\end{figure}
-
-	%BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
-	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
-	\begin{itemize}
-		\item Phase A
-		\begin{itemize}	
-			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
-			\item There is evidence that the stacked configuration will shift towards an offset configuration over time.
-WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
-			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
-			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
-		\end{itemize}
-		\item Phase B
-		\begin{itemize}
-			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
-			\item No spots at all which is consistent with the disorder shown by the rings in the pore
-		\end{itemize}
-		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\textsuperscript{-1} which is typical of packed alkane chains
-		\item Both phases exhibit axial reflections.
-Even though the rings are not ordered in phase B, they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present
-	\end{itemize}
-
-	\begin{figure}
-	\centering
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:xrdA}}
-	\end{subfigure}
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:xrdexp}}
-	\end{subfigure}
-        \begin{subfigure}{.3\textwidth}
-                \centering
-                \includegraphics[width=\linewidth]{placeholder.png}
-                \caption{~\label{fig:xrdB}}
-        \end{subfigure}
-	\caption{Phase A (a) provides a good match to experiment (b). Phase B (c) is missing reflections present in the experimental pattern} % BJC: any more detail? 
-	\label{fig:xrd}
-	\end{figure}
-
-	The model gives reasonable estimates of ionic conductivity for both phases.
-	\begin{itemize}
-		\item See comparison of methods in Table~\ref{table:conductivity}
-		\item The methods agree reasonably well within error
-		\item In the future, we will probably only use Nernst Einstein because it requires less simulation to get good statistics. %BJC: probably don't need to mention this
-		\item Our calculated values are higher than experimental values, as expected.
-		\item The real system, although mostly aligned and straight, still has a distribution of azimuthal angles, lowering the effective ionic conductivity of the bulk membrane. 
-		\item The ordering from isotropic to mostly aligned mesophases showed an 85x increase in ionic conductivity. We would expect more gains in a perfect system.
-		\item The ordered phase has a higher calculated ionic conductivity than the disordered phase.
-	\end{itemize}
-
-	\begin{table}
-	\centering
-	\begin{tabular}{|c|c|}
-	\hline
-	Nernst Einstein & Collective Diffusion \\
-	\hline
-	\end{tabular}
-	\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error.
-Both methods give calculated values of ionic conductivity which are higher than experimental values~\label{table:conductivity}}
-	\end{table}
-
-	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies.
-Using the design framework and analysis methods applied herin, we have the ability to reliably predict structures of new nanoporous membranes.
-
-	\section{Conclusion}
-
-	In this work, we have suggested a more detailed picture of the structure of a self assembled thermotropic liquid crystal membrane using an atomistic molecular model.
-	\begin{itemize}
-		\item The model's physical properties are consistent with experimental measurements
-		\item We have discovered the existence of two metastable configurations that persist at room temperature
-		\item This methodology has been developed for a specific case but can be readily adapted to other LLCs
-	\end{itemize}
-	% focus around what we learned about the system - not that we have a model
-
-	\section{Supplemental Information}
-
-	Monomer configurations
-	\begin{itemize}
-		\item Pore-to-pore equilibration plots
-		\item Plots of other things that level off indicating equilibration
-		\item 3D visualizations of different configurations tested
-		\item Sodium ion distribution in disordered phase
-	\end{itemize}
-
-        \begin{figure}
-		\centering
-		\includegraphics{placeholder.png}
-                \caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
-                \label{fig:initial}
-        \end{figure}
-
-	\noindent Crosslinking details
-	\begin{itemize}
-		\item Algorithm description. Link to full algorithm in git repository
-		\item A figure showing the new crosslinks
-	\end{itemize}
-
-	\noindent Ionic conductivity % plus more details on implementation.
-	\begin{itemize}
-		\item MSD plots
-	\end{itemize}
-\end{document}

### 2017-05-05 Ben_Manuscripts/Paper1/intro.tex
intro drafted

@@
 Nanostructured membrane materials have become increasingly popular for 
-aqueous separations applications because they offer the ability to 
-control membrane architecture at the atomic scale allowing design of 
-solute-specific separation membranes \cite{humplik_nanostructured_2011}.
-Most membrane-based aqueous separations of small molecules can be 
-achieved using reverse osmosis (RO) or nanofiltration (NF).
+aqueous separations applications such as desalination and biorefinement
+because they offer the ability to control membrane architecture at the
+atomic scale allowing design of solute-specific separation membranes 
+\cite{humplik_nanostructured_2011}. Most membrane-based aqueous 
+separations of small molecules can be achieved using reverse osmosis 
+(RO) or nanofiltration (NF)\cite{van_der_bruggen_review_2003}.
 
@@
 RO membranes are unstructured with tortuous and polydisperse diffusion
-pathways which can lead to inconsistent performance. Tortuosity and 
-polydispersity drive up energy requirements which strain developing regions and 
-contribute strongly to CO\textsubscript{2} emissions. Designing RO 
+pathways which leads to inconsistent performance\cite{song_nano_2011}.
+Necessarily high feed pressures drive up energy requirements which 
+strain developing regions and contribute strongly to CO\textsubscript{2} 
+emissions\cite{mcginnis_global_2008}. Moreover, designing RO 
 membranes to achieve targeted separations of specific solutes is nearly
-impossible. Various solutes dissolve into and diffuse through the polymer
-matrix at different rates. At best, one can exploit these differences 
-to create a functional selective barrier. NF was introduced as an 
-intermediate between RO and ultrafiltration (UF), having the abilitiy to
-separate organic matter and salts on the order of one nanometer in size.
-Larger and well-defined pores drive down energy requirements while still
-affording separation of solutes as small as ions to some degree. This is
-why NF is often used as a precursor to reverse osmosis. Unfortunately,
-NF membranes, like RO, are produced with a pore size distribution which 
-limits their ability to perform precise separations.
+impossible because various solutes dissolve into and diffuse through the polymer
+matrix at different rates\cite{wijmans_solution-diffusion_1995}. At best,
+one can exploit these differences to create a functional selective 
+barrier. NF was introduced as an intermediate between RO and 
+ultrafiltration, having the ability to separate organic matter and salts
+on the order of one nanometer in size. Larger and well-defined pores 
+drive down energy requirements while still affording separation of 
+solutes as small as ions to some degree\cite{van_der_bruggen_review_2003}.
+This is why NF is often used as a precursor to reverse osmosis. 
+Unfortunately, NF membranes, like RO, are produced with a pore size 
+distribution which limits their ability to perform precise separations
+\cite{bowen_modelling_2002}.
 
@@
 to synthesize and scale various fundamentally sound technologies.
-Graphene sheets are atomically thick which gives excellent permeability
+Graphene sheets are atomically thick which results in excellent permeability
 but defects during manufacturing severely impact selectivity 
@@
 Zeolites have sub-nm pores with a narrow size distribution and MD simulations
-exhibited complete rejection of solvated ions \cite{murad_molecular_1998},
+exhibit complete rejection of solvated ions \cite{murad_molecular_1998},
 however, experimental rejection was low and attributed to interstitial
@@
 structures with the added benefits of low cost and synthetic techniques
-feasible for large scale production.
-\begin{itemize}
-	\item LLCs are versatile and controllable with a large chemical design space available for membrane design
-	\item Synthetic techniques are cheap and amenable to creating any monomer in this large design space
-	\item LLCs forms lamellar, bicontinuous cubic and hexagonal phases based on solution composition
-	\item Na-GA3C11 has been described in literature as forming two types of self assembled phases - thermotropic (Colh) and lyotropic (HII)
-	\item The thermotropic, Colh, is formed by the self assembly of neat monomer
-	\item The lyotropic, HII phase is formed in the presence of small amounts of water
-	\item Both assemble into cylinders with hydrophilic groups oriented inward towards the pore center and hydrophobic groups facing outward.
-The only difference is the inclusion of water in the structure which leads to minor variations in the structure with potentially different filtration properties (although no filtration experiments have been done on Colh)
-	\item Hydrophilic regions point towards pore centers
-	\item Until recently, they could not be aligned - hindered progress
-	\item Yale aligns them, then crosslinks them to lock in the structure - reference 2014 and 2016 papers. They say that they are scalable techniques
-	\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
-	\item The Colh phase shares the same structural features with the HII phase with the exception of the presence of water.
-This paper will focus on the development of a model of the Colh phase since it is a simpler starting point and has just as much experimental data.
-The analysis used in this paper can be readily extended to the HII phase.
-\end{itemize}
+feasible for large scale production\cite{feng_scalable_2014}. LLCs are
+versatile and controllable with a large chemical design space available
+for membrane design. We will be studying assemblies formed by Na-GA3C11 
+(Figures~\ref{fig:chemdraw} and ~\ref{fig:monatomistic}), a system which
+has been extensively studied experimentally\cite{smith_ordered_1997,
+zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
+Neat monomer forms the thermotropic, Col\textsubscript{h} phase. The 
+presence of small amounts of water results in the H\textsubscript{II} 
+phase. In both cases, monomers assemble into mesophases made of 
+hexagonally packed cylinders with hydrophilic groups oriented inward
+towards the pore center and hydrophobic groups facing outward. Until
+% BJC: reproduce the figure from ACS nano? It does a good job
+% BJC: I can also color in the atomistic layer a bit 
+recently, the mesophases could not be macroscopically aligned, resulting
+in a low flux membrane, slowing research in the field. In 2014, 
+Feng et al. showed that the mesophases could be aligned using a magnetic
+field with subsequent crosslinking to lock the structure in place
+\cite{feng_scalable_2014}. In 2016, Feng et al. showed that the same 
+result could be obtained using a technique called soft confinement
+\cite{feng_thin_2016}. Following this breakthrough, research into LLC
+membranes has been reinvigorated. This paper will focus on 
+the development of a model of the Col\textsubscript{h} phase membrane
+meant to accelerate development of LLC membranes. We have chosen to 
+model the Col\textsubscript{h} phase since it is a simpler starting 
+point and has just as much experimental structural data as the 
+H\textsubscript{II} phase.
 
-A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines to reduce the chemical space for design of monomers used to create separation-specific membranes.
-\begin{itemize}
-        \item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effective water desalination and small organic separations.
-Rejection studies show that this membrane can not do desalination yet
-%MRS: ^^^nice way to turn a weakness of the materials class into an opportunity to improve them requring research! 
-	\item Colh phase studies currently limited to one monomer
-        \item Optimization efforts performed through trial and error over the past 20 years
-        \item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
-        \begin{itemize}
-                \item What does the microscopic pore structure look like?
-		\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
-		\item Is rejection of ions due to donnan exclusion?
-                \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
-                \item Is water structured inside the pores, restricting low energy pathways for solutes to follow? %BJC: saw something like this in a paper
-	\end{itemize}
-	\item How can microscopic pore structure guide membrane design
-	\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
-	\item We can use molecular dynamics simulations to enhance our understanding 
-\end{itemize}
+\begin{figure}
+\centering
+\begin{subfigure}{.45\linewidth}
+	\centering
+        \includegraphics[width=\linewidth]{placeholder.png}
+        \caption{}\label{fig:chemdraw}
+\end{subfigure}
+\begin{subfigure}{.45\linewidth}
+	\centering
+        \includegraphics[width=\linewidth]{placeholder.png}
+        \caption{}\label{fig:monatomistic}
+\end{subfigure}
+\medskip
+\begin{subfigure}{.45\linewidth}
+	\centering
+        \includegraphics[width=\linewidth]{placeholder.png}
+        \caption{}\label{fig:cartoonlayer}
+\end{subfigure}
+\begin{subfigure}{.45\linewidth}
+	\centering
+        \includegraphics[width=\linewidth]{placeholder.png}
+        \caption{}\label{fig:layeratomistic}
+\end{subfigure}
+\caption{(a) The chemical structure of NAGA3C11 (b) The chemical 
+structure visualized atomistically enhances intuition about system
+behavior (c) Wedge-shaped monomers assemble into layers (d) An atomistic
+view of a layer suggests geometric constraints based on monomer
+structure}\label{fig:cartoonvatomistic}
+\end{figure}
+%BJC: maybe add 2 more panels with full assemblies represented with
+% a cartoon and atomistically
 
-A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms.
-\begin{itemize}
-	\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
-	\begin{itemize}
-		\item This could change how one thinks about molecules diffusing through membrane
-		\item Could also be a difference between lyotropic and thermotropic phases
-	\end{itemize}
-	\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
-	\begin{itemize}
-		\item How do the monomer head groups pack together? Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
-		\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
-		\item Substituted benzene rings exhibit an even stronger pi-stacking attraction %BJC: reference ab initio papers   	
-		\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
-		\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer % reference 2005-ish Zhou paper 
-	\end{itemize}
-	\item It is possible there is more than one metastable states associated with this LLC system
-	\begin{itemize}
-		\item Which phase is consistent with experiment?
-		\item Can both phases be created experimentally?
-		\item How will each state affect transport?
-	\end{itemize}
-\end{itemize}
+A molecular level understanding of LLC membrane structure will elucidate
+small molecule transport mechanisms, providing guidelines to reduce the
+chemical space for design of monomers used to create separation-specific
+membranes. We do not yet understand how to reduce the effective pore
+size or tune the chemical environment in the H\textsubscript{II} 
+nanopores for effective water desalination and small organic separations.
+Rejection studies show that this membrane can not perform desalination yet 
+because the pores are too large\cite{zhou_supported_2005}. Over the past
+20 years, LLC membrane studies have been limited primarily 
+to Na-GA3C11 with some characterization done after minor structural 
+modifications\cite{resel_structural_2000}. Optimization has been 
+performed through trial and error. The only source of predictive modeling
+has been macroscopic models which likely do not adequately describe 
+transport at these length scales. A good model should incorporate a 
+detailed picture of the nanoscopic pore structure. Pore components may 
+play a role in rejection of charged or uncharged solutes. Choice of 
+counterion may influence the establishment of a donnan potential
+affecting the degree to which the membrane can exclude charged species.
+Moieties inside the pores may interact with neutral solutes, rejecting
+% BJC: (so I can remember this theory in the future) A donnan potential
+% is established when the same ions are present on either side of a barrier.
+% Pretend you have a bath of NaCl separated by a semipermeable membrane from
+% a bath of NaPr where Pr is a protein. Sodium will first cross to the side
+% with less sodium down a concentration gradient. This will cause a
+% charge imbalance which will cause sodium ions to cross back to the other 
+% side down an electric potential gradient. Eventually this movement 
+% reaches an equilibrium and a Donnan potential is established since the 
+% charge will likely be unbalanced. In the context of the HII membrane, we
+% will have a bunch of sodium counterions in the pores and a bath of NaCl
+% above the membrane. In most cases, except in high concentrations of bulk
+% NaCl, sodium ions from the pore will leave the membrane down a conc gradient.
+% Some will go back in, but the resulting system will be a net negatively charged
+% membrane with a net positive charge in the bulk solution (at least close to
+% the membrane-salt water interface). Sodium ions will be rejected from the 
+% bulk due to charge exclusion despite a concentration gradient on either 
+% side of the membrane.
+rejecting on the basis of shape and size, rather than just hydrodynamic
+radius. An atomistic understanding of pore structure and its influence on
+% BJC: probably leave this point out since it involves a solvated system: 
+% Is water structured inside the pores, restricting low energy pathways
+% for solutes to follow? 
+transport can help identify performance bottle necks and direct design of
+future membranes.
 
-We must show that the developed molecular model is consistent with physical observations so that we can trust conclusions drawn about structural features characteristic of the system.
-\begin{itemize}
-	\item This paper will illustrate the development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
-	\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
-	\item We are primarily interested in reproducing the conclusions about structure which have been made from XRD experiments and ionic conductivity measurements.    
-	\item We have comparied simulated X-ray diffraction patterns to experiment in order to match major features present in the 2D patterns
-	\item We can predict ionic conductivity using two agreeing methods -- Collective diffusion and nernst einstein
-	\item We examined crosslinking mechanism and understand its influence on membrane structure
-\end{itemize}
+%BJC: I dont like this sentence vvv
+A clear picture of the nanoscopic structure of LLC membranes, gained by
+building a molecular model, will provide evidence to support or call
+into question past drawn conclusions that have largely guided our 
+understanding of separation mechanisms.	The arrangement of sodium ions
+in the channels is thought to be confined to the pore walls. It is 
+possible they are arranged more randomly. This would change the way
+one thinks about molecules diffusing through the membrane. The
+Col\textsubscript{h} phase is described as having pores made of disks or
+layers (Figure~\ref{fig:cartoonlayer},~\ref{fig:layeratomistic}) stacked
+on top of one another, each containing a set number of monomers. A 
+simple simulation study of a similar molecule suggests that there are 4
+monomers in each disk~\cite{zhu_methacrylated_2006}. A separate calculation
+based on the volume of the liquid crystal monomers proposes that there 
+are seven monomers in each layer~\cite{resel_structural_2000}. Once we 
+know the number of monomers in each layer, we still do not know how 
+monomers in each layer are positioned with respect to other layers. 
+One of the driving forces for self % reference something with self assembly of aromatic compounds
+assembly in this system is thought to be pi-stacking interactions
+between headgroup benzene rings\cite{gazit_possible_2002}. Gas phase ab
+initio studies of benzene dimers have shown a clear energetic advantage
+for parallel displaced and T-shaped pi-stacking conformations versus a
+sandwiched conformation~\cite{sinnokrot_estimates_2002}.
+Substituted benzene rings exhibit an even stronger pi-stacking 
+attraction which favors the parallel displaced configuration in all cases
+except where the substitutions are extremely electron withdrawing
+\cite{waller_hybrid_2006,ringer_effect_2006}. While we might be able to
+provide answers to these questions using a molecular model, there remains
+the possibility that there is more than one metastable state associated
+with a given LLC system. We must be able to identify which states can
+%BJC: might get rid of this last point since we don't address experimental viability of metastable states
+be produced experimentally and what implications each state might have
+regarding transport properties.
+
+We must show that the developed molecular model is consistent with
+physical observations so that we can trust conclusions drawn about 
+structural features characteristic of the system. This paper will
+illustrate the development of a predictive molecular model and the steps
+taken to ensure it mimics the real system within the constraints 
+inherent to MD. To understand how physically realistic the model is,
+validation by comparison to experiment is necessary. We are primarily
+interested in reproducing the conclusions about structure which have been
+made from XRD experiments and ionic conductivity measurements
+\cite{feng_thin_2016}. We have comparied simulated X-ray diffraction
+patterns to experiment in order to match major features present in the
+2D patterns. We calculate ionic conductivity using two agreeing methods.
+We examined the crosslinking mechanism and understand its influence on
+membrane structure. The analysis used in this paper can be readily
+extended to the H\textsubscript{II} phase.

### 2017-05-06 Ben_Manuscripts/Outlines/Paper1_Outline.tex
Added comments.

@@
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joseph Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
+%MRS2: might need Osuji on this -- you can ask Xunda.  Check with people's published work on whether they use their middle initial. 
 \begin{document}
@@
 	\begin{itemize}
-		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
-		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
+		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to 
+%MRS2: is inconsistent the right word?
+inconsistent performance
+		\item Tortuosity and polydispersity drive up energy requirements which 
+%MRS2: are ``strain developing regions'' the right words?
+strain developing regions and contribute strongly to CO2 emissions
 		\item Designing RO membranes to achieve targeted separations of specific solutes is nearly impossible due to the separation (hypothesized to be) controlled by fluctuating polymer voids
@@
                 %MRS: Doug should have information on the chemistry here and how resistant they might be.
-		%BJC: Doug said they didn't do any chemical stability testing since the membranes had flux problems in the first place. So I won't mention this
-		\item nanofiltration was introduced as an intermediate between RO and ultrafiltration
+		%BJC: Doug said they didn't do any chemical stability testing since the membranes had flux problems in the first place. So I won't mention this.
+                %MRS2: sounds good.  Or could simply say (somewhere) that a greater variety of chemistries are needed to handle diverse types of inflow streams.
+		\item Nanofiltration was introduced as an intermediate between RO and ultrafiltration
 		\item Larger and well-defined pores drive down energy requirements while still affording separation of solutes as small as ions, to some degree
@@
 		\item The thermotropic, Colh, is formed by the self assembly of neat monomer
-		\item The lyotropic, HII phase is formed in the presence of small amounts of water
+                  %MRS2: small change below.
+		\item The lyotropic, HII phase is formed without (or in practice, with very small amounts of water)
 		\item Both assemble into cylinders with hydrophilic groups oriented inward towards the pore center and hydrophobic groups facing outward.
@@
 		\item Hydrophilic regions point towards pore centers
+                  %MRS2: Be more specific on ``hindered progress'' 
 		\item Until recently, they could not be aligned - hindered progress
@@
 			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
-			\item Is rejection of ions due to donnan exclusion?
+%MRS2: ``related to ionic conduction'' is vague
+			\item Is rejection of ions due to Donnan exclusion?
                         \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
-                        \item Is water structured inside the pores, restricting low energy pathways for solutes to follow? %BJC: saw something like this in a paper
+                        \item Is water structured inside the pores, restricting low energy pathways for solutes to follow? 
+%BJC: saw something like this in a paper 
+%MRS2: good, cite if you can.
 		\end{itemize}
-		\item How can microscopic pore structure guide membrane design
+		\item How can microscopic pore structure guide membrane design?
+                  \begin{itemize}
 		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
@@
                   \end{itemize}
+	\end{itemize}
 
-	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms.
+	A clear picture of the nanoscopic structure of LLC membranes, gained by building 
+%MRS2: suggest ``molecular models'', as one can argue that each way of doing it is a different model, or that it might require trying 2-3 things.
+a molecular model, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
 	\begin{itemize}
+%MRS2: a thought - it would be great to add what is exactly meant by ``pore walls'' and how well defined they are is not clear.
+For example, how strict is the division between the hydrophobic tails, the head groups, and the ionic groups?
+This directly affects what is meant by the ``size'' of the nanopore, and (to put somewhere else in the outline) what size exclusion means.
  		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
@@
 	\end{subfigure}
-	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition about system behavior (c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests geometric constraints based on monomer structure}\label{fig:cartoonvatomistic}
+	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition about system behavior %MRS2: in what way?
+(c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests geometric constraints based on monomer structure %MRS2: suggests what?}\label{fig:cartoonvatomistic}
 	\end{figure}
@@
 	\begin{itemize}
+          %MRS2: specify what type of self assembly -- could be that layers are faster than hexagonal pores to get to.
 		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
@@
 
+%MRS2: need to be careful describing which stacking/layering is described where/when based on experiments actually reported.
 	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
@@
                 \item Decided on 20 layers using a system which held a vacuum gap above and below the membrane
-                \item Too few layers leads to micelle-like formations
+                \item Too few layers leads to micelle-like formations %MRS: with gap.
 	\end{itemize}
@@
 	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
+%MRS2: ``treated as variables'' is vague. Be specific about what it means you are doing.
 	\begin{itemize}
-		\item XRD gives Pore-to-Pore distances of $\approx$ 4.1 nm and indicates possible pi-stacking at $\approx$ 3.7 \angstrom (see figure~\ref{fig:xrd}) on - comparison of experimental vs. simulated)
+		\item XRD gives pore-to-pore distances of $\approx$ 4.1 nm and indicates possible pi-stacking at $\approx$ 3.7 \angstrom (see figure~\ref{fig:xrd}) on - comparison of experimental vs. simulated)
 		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
@@
         \begin{itemize}
-               \item 3 dimensional fourier transformed electron density generates simulated 1D and 2D diffraction patterns
+               \item 3 dimensional Fourier transformed electron density generates simulated 1D and 2D diffraction patterns
                \item The 1D patterns are generated by spherical integration of the FT
@@
                \item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
+                 %MRS2: ``iterative improvement'' is vague -- other researchers could not implement that (unless you say you give details elsewhere)
         \end{itemize}
@@
                         \item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores.
-One would expect single channel IC to be much larger than the bulk membrane
+One would expect single channel IC to be much larger than the bulk membrane %MRS: per area, since extensively, bulk would be be bigger (multiple pores)
                 \end{itemize}
@@
 	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
+%MRS2: higher radial disorder - make clear still hydrophobic/hydrophilic.
         	\begin{itemize}
@@
                 	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
+                          %MRS2: below: ``Only difference''.
+Only difference is in how they are prepared.
+But presumably, there are a number of initial configurations that can lead to this one, so emphasizing that it's the only difference isn't that important.
+Also, we want to be emphasizing the thermodynamic differences, not kinetics.
                 	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the initial interlayer spacing
@@
         \begin{itemize}
-		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a clear relation between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here
+		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a 
+%MRS2: ``clear relation'' is a bit indirect. 
+clear relation between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here %MRS2: yep, refer a figure here.
 		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
@@
 		\item Simulating the system at room temperature should be sufficient to see both phases
+                  %MRS2: what does ``sufficient'' mean here?  Sufficient for what purpose?
 	\end{itemize}
 
-	A summary of all experiments and relevant structural parameters are presented in table ~\ref{table:p2p}
+        %MRS2: Tables should also have specific theses as well, so think about that.  Merely saying ``here is the information'' isn't as useful without a guide through it.
+	A summary of all experiments and relevant structural parameters are presented in Table ~\ref{table:p2p}
 
@@
 An order parameter of 1 indicates perfect ordering, while 0 indicates disorder}\label{fig:transition}
+%MRS2: maybe provide a bit more information what data will be here?  Order parametr vs time? One panel with order paramter vs. time, one with configurations from 0 and 1 endpoints?
 	\end{figure}
@@
 	\end{tabular}
+        %MRS2: what is the thesis here?
 	\caption{A system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data}\label{table:p2p} 
@@
 	\caption{There are clear differences in pore structure between systems built with layers stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
+        %MRS2: explain theses?
+Also, the exact configurations used to start them are probably not that important; many different initial configurations will probably lead to most of them.
+It's the thermodyamics that are important.
 	\label{fig:porestructures}
@@
 	%BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
+        %MRS2: a little hard to say until the data is in.
 	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
@@
 		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\textsuperscript{-1} which is typical of packed alkane chains
-		\item Both phases exhibit axial reflections.
-Even though the rings are not ordered in phase B, they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present
+		\item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B, 
+%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
+they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present   
+%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
 	\end{itemize}
@@
         \end{subfigure}
-	\caption{Phase A (a) provides a good match to experiment (b). Phase B (c) is missing reflections present in the experimental pattern} % BJC: any more detail? 
+	\caption{Phase A (a) provides a good match to experiment (b).
+Phase B (c) is missing reflections present in the experimental pattern} % BJC: any more detail?
+%MRS2: yes, give distances, and describe what you mean as ``good match''
 	\label{fig:xrd}
@@
 		\item The methods agree reasonably well within error
-		\item In the future, we will probably only use Nernst Einstein because it requires less simulation to get good statistics. %BJC: probably don't need to mention this
+		\item In the future, we will probably only use Nernst Einstein because it requires less simulation to get good statistics.
+%BJC: probably don't need to mention this %MRS2: can mention it peforms better, informing future work.
 		\item Our calculated values are higher than experimental values, as expected.
@@
 Both methods give calculated values of ionic conductivity which are higher than experimental values~\label{table:conductivity}}
+%MRS2: I would say that they are reasonable close to experiment, though higher. Also somewhat contradicted in other places.
 	\end{table}
@@
 		\item The model's physical properties are consistent with experimental measurements
+                  %MRS2: are these two disordered and offset?  If so, then one is stable (Though we are not sure at 300K which is which).  Or are you referring to three phases?
 		\item We have discovered the existence of two metastable configurations that persist at room temperature
@@
 	\end{itemize}
-	% focus around what we learned about the system - not that we have a model
+	%MRS: focus around what we learned about the system - not that we have a model
 
-	\section{Supplemental Information}
+	\section{Supplemental Information} %MRS2: check, might be called supporting information, depending on the journal.
 
@@
                 \caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
+                %MRS2: what is the thesis?
                 \label{fig:initial}

### 2017-05-11 Ben_Manuscripts/Outlines/Paper1_Outline.tex
Outline edits

@@
 
-	Nanostructured membranes can bypass many of the performance issues which plague traditional NF and RO membranes.
+	Nanostructured membranes can bypass many of the performance issues which plague traditional NF and RdO membranes.
 	\begin{itemize}
@@
 			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
-%MRS2: ``related to ionic conduction'' is vague
 			\item Is rejection of ions due to Donnan exclusion?
@@
 %MRS2: suggest ``molecular models'', as one can argue that each way of doing it is a different model, or that it might require trying 2-3 things.
-a molecular model, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
+molecular models, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
 	\begin{itemize}
@@
 	%BJC: I'm not sure where to place this figure. ACS nano requires the methods section to go last (after conclusions). It seems like this should go earlier, but it fits the context best around here.
+	%BJC2: I think I might make this a six panel figure. The other two panels will show a cartoon and atomistic pore view.
 	\begin{figure}
@@
 	\end{subfigure}
-	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition about system behavior %MRS2: in what way?
-(c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests geometric constraints based on monomer structure %MRS2: suggests what?}\label{fig:cartoonvatomistic}
+	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition how monomers might pack together %MRS2: in what way?
+(c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests a reasonable range of monomers per layer to test\label{fig:cartoonvatomistic}  
 	\end{figure}
@@
           %MRS2: specify what type of self assembly -- could be that layers are faster than hexagonal pores to get to.
+	  %BJC2: Don't I suggest the type of self assembly to be assembly into the hexagonal phase? Or should I be more broad as in, we see no type of self-assembly occuring.
 		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
@@
 %MRS2: need to be careful describing which stacking/layering is described where/when based on experiments actually reported.
+%BJC2: can you clarify this point?
 	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
@@
 
-	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and treated as variables during model development 
+	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and varied in order to develop a model that agrees with experiment. 
 %MRS2: ``treated as variables'' is vague. Be specific about what it means you are doing.
@@
                \item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
-               \item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
-                 %MRS2: ``iterative improvement'' is vague -- other researchers could not implement that (unless you say you give details elsewhere)
+               \item We matched experiment by varying the initial structure. The selection of initial structure is explained later
         \end{itemize}
@@
                 \item This will be called phase A for simplicity  
-	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
-%MRS2: higher radial disorder - make clear still hydrophobic/hydrophilic.
+	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder, while maintaining partitioning between hydrophobic and hydrophilic regions.
         	\begin{itemize}
@@
 Also, we want to be emphasizing the thermodynamic differences, not kinetics.
-                	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the initial interlayer spacing
+                	\item Like phase A, phase B can form at 280K. %BJC2: ^^ so get rid of this part : The only difference in simulations leading to this state, is the initial interlayer spacing
                 	\item The phase is also present when phase A is heated close to its isotropic transition point
@@
 %MRS2: ``clear relation'' is a bit indirect. 
-clear relation between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here %MRS2: yep, refer a figure here.
+%BJC2: clear link? 
+clear link between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here %MRS2: yep, refer a figure here.
 		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
@@
 	\centering
+	\begin{subfigure}
+		\centering
 		\includegraphics[width=\linewidth]{placeholder.png}
-	\caption{As temperature is increased, Phase A transitions to Phase B, as indicated by the shown order parameter.
-An order parameter of 1 indicates perfect ordering, while 0 indicates disorder}\label{fig:transition}
+		\caption{}\label{fig:orderparameter}
+	\end{subfigure}
+	\begin{subfigure}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{}\label{fig:order}
+	\end{subfigure}
+	\begin{subfigure}
+		\centering
+		\includegraphics[width=\linewidth]{placeholder.png}
+		\caption{}\label{fig:disorder}
+	\end{subfigure}
+	\caption{(a) As temperature is increased, Phase A transitions to Phase B, becoming more disordered.
+An order parameter of 1 indicates perfect ordering, while 0 indicates disorder.
+(b) The system is ordered, characteristic of Phase A, initially (c) The system becomes disordered, characteristic of Phase B, as temperature is raised beyond 310K}\label{fig:transition}
 %MRS2: maybe provide a bit more information what data will be here?  Order parametr vs time? One panel with order paramter vs. time, one with configurations from 0 and 1 endpoints?
@@
 	\end{tabular}
-        %MRS2: what is the thesis here?
-	\caption{A system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data}\label{table:p2p} 
+	\caption{The pore spacing of the model increases as number of monomers in each layer increases.
+The pore spacing of a system starting in the sandwiched configuration is systematically lower than that started in an offset configuration.
+Systems built with 5 monomers per layer in a parallel displaced configuration results in a pore spacing closest to experimental data}\label{table:p2p}
 	\end{table}
@@
 It's the thermodyamics that are important.
+	%BJC: okay, so just rephrase it, worded in a way that doesn't reference the initial configuration/layer spacing?
+	%BJC: what do you  mean by 'thermodynamics that are important' -- just distinguishing which state is more favorable under what conditions?
 	\label{fig:porestructures}
@@
 %MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
+%BJC2: Are you thinking about the fourier transforms? I could bring that in
 	\end{itemize}
@@
 %MRS2: yes, give distances, and describe what you mean as ``good match''
+%BJC2: what is a clear way to describe the spots in the ring. Diagonal reflections? radial spots?
 	\label{fig:xrd}
@@
 	\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error.
-Both methods give calculated values of ionic conductivity which are higher than experimental values~\label{table:conductivity}}
+Both methods give calculated values of ionic conductivity which are higher, but reasonably close to experimental values~\label{table:conductivity}}
 %MRS2: I would say that they are reasonable close to experiment, though higher. Also somewhat contradicted in other places.
@@
 
-	\section{Supplemental Information} %MRS2: check, might be called supporting information, depending on the journal.
+	\section{Supplemental Information} %MRS2: check, might be called supporting information, depending on the journal. %BJC2: Also, it's a separate document in ACS nano at least
 
@@
 
+	Equilibration procedure
+
 	\noindent Crosslinking details

### 2017-06-21 Ben_Manuscripts/Paper1/results.tex
added results

--- 2017-05-11 Ben_Manuscripts/Outlines/Paper1_Outline.tex
@@
-\documentclass{article}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{geometry}
-\geometry{legalpaper, margin=1in}
-\usepackage{amsmath} % or simply amstext
-\newcommand{\angstrom}{\textup{\AA}}
-\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joseph Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
-%MRS2: might need Osuji on this -- you can ask Xunda.  Check with people's published work on whether they use their middle initial. 
-\begin{document}
-	\bibliographystyle{ieeetr}
-	\graphicspath{{./figures/}}
-	\maketitle
-	\section{Introduction}
-	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale allowing design of solute-specific separation membranes.
+\section{Results and Discussion}
 
-	While RO anad NF have seen many advances in the past few decades, they are far from perfect separation technologies
+In order to construct an initial configuration which gives reliable 
+trends, we need to understand the composition of layers, how far apart
+to stack the layers, and how to orient them with respect to each other.
+
+The initial distance between layers can influence the approach towards
+equilibrium. In the real system, according to wide angle X-ray
+scattering (WAXS) experiments, layers are stacked 3.7 \angstrom apart.
+A characteristic of equilibrated systems simulated in this way, is a
+defined, cylindrical and open pore structure. Benzene rings arrange in
+a helical conformation after equilbration. The membrane is about 8 nm
+thick. We will refer to this system as Phase A. (Fig ~\ref{fig:phaseA})
+Simulations of systems built with layers stacked > 4 \angstrom apart
+results in a pore structure characterized by high radial disorder,
+while maintaining partitioning between hydrophobic and hydrophilic
+regions. This will be called phase B (Fig~\ref{fig:phaseB})
+% The arrangement of sodium ions (which are closely bound to carbonyl
+% head groups) can be well-approximated by a gaussian distribution 
+It is apparent that this LLC membrane may exist in at least two
+metastable states. The distinct difference in pore structure exhibited
+by each phase will likely lead to different transport mechanisms.
+Understanding which phase exists experimentally is necessary in order
+to appropriately study the system.
+%Like phase A, phase B can form at 280K. 
+%The phase is also present when phase A is heated close to its isotropic transition point
+%There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
+
+        Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
         \begin{itemize}
-		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to 
-%MRS2: is inconsistent the right word?
-inconsistent performance
-		\item Tortuosity and polydispersity drive up energy requirements which 
-%MRS2: are ``strain developing regions'' the right words?
-strain developing regions and contribute strongly to CO2 emissions
-		\item Designing RO membranes to achieve targeted separations of specific solutes is nearly impossible due to the separation (hypothesized to be) controlled by fluctuating polymer voids
-		\item RO has difficulty separating neutral organics because they tend to dissolve in polymer matrix
-		\item Many current RO membranes degrade in typical chlorine filled municipal water supplies (debating this point because there aren't any studies of LLC membrane fouling resistance)
-                %MRS: Doug should have information on the chemistry here and how resistant they might be.
-		%BJC: Doug said they didn't do any chemical stability testing since the membranes had flux problems in the first place. So I won't mention this.
-                %MRS2: sounds good.  Or could simply say (somewhere) that a greater variety of chemistries are needed to handle diverse types of inflow streams.
-		\item Nanofiltration was introduced as an intermediate between RO and ultrafiltration
-		\item Larger and well-defined pores drive down energy requirements while still affording separation of solutes as small as ions, to some degree
-		\item Like RO membranes, NF membranes have a pore size distribution which limits their ability to perform precise separations
+                \item Phase A
+                \begin{itemize}
+                        \item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
+                        \item There is evidence that the stacked configuration will shift towards an offset configuration over time.
+WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
+                        \item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
+                        \item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
+                \end{itemize}
+                \item Phase B
+                \begin{itemize}
+                        \item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
+                        \item No spots at all which is consistent with the disorder shown by the rings in the pore
+                \end{itemize}
+                \item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom \textsuperscript{-1} which is typical of packed alkane chains
+                \item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B,
+%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
+they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present
+%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
+%BJC2: Are you thinking about the fourier transforms? I could bring that in
         \end{itemize}
 
-	Nanostructured membranes can bypass many of the performance issues which plague traditional NF and RdO membranes.
-	\begin{itemize}
-		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
-		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
-		\item Entirely different mechanisms govern the separation processes in various nanostructured materials which can inspire novel separation techniques
-	\end{itemize}
+We varied the relative interlayer orientation between sandwiched and 
+parallel-displaced based on our knowledge of the stability of these two
+pi-stacking modes. Short simulations were run with position restraints
+on benzene rings. Simulated X-ray diffraction patterns generated from 
+each configuration establishes a link between the parallel displaced 
+stacking mode and major features present in experimental XRD patterns.  % FIGURE!!!!!!!!!!
+The faint ring at a distance of $\approx$ 1.5 \angstrom \textsuperscript{-1} 
+is commonly identified as a result of the average packing distance 
+between alkane chains. Four spots of higher intensity are visible in the 
+alkane chain region creating an x-shaped pattern. The spots are only
+generated for structures created in the parallel displaced configuration.
+In the past, the spots have been attributed to the tilt angle of the 
+alkane chains. Theoretically the angle is the same as that made between 
+the spots and the x-axis. However, we achieved the same pattern with 
+a calculated average tilt angle of 0 $\pm$ 9 degrees. % GET THE RIGHT NUMBER !!!!!
 
-	Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
-	\begin{itemize}
-		\item Leading technologies and their limitations:
-		\begin{itemize}
-			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact selectivity
-			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
-			\item Zeolites - sub-nm pores with good MD results but interstitial defects created during manufacturing kill selectivity 
-		\end{itemize}
-	\end{itemize}
+Further simulation indicates that both configurations are stable for 
+100's of nanoseconds. Simulated diffraction of the sandwiched 
+configuration after equilibration shows the spots which were not initially
+present, implying that there is a shift towards the parallel-displaced
+mode. To quantify the degree of sandwiched stacking, we measured the 
+amount of overlap between projections of benzene rings and those below
+them. The amount of overlap between projections decreases rapidly. % FIGURE !!! overlap
 
-	Self assembling lyotropic liquid crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques feasible for large scale production.
-	\begin{itemize}
-		\item LLCs are versatile and controllable with a large chemical design space available for membrane design
-		\item Synthetic techniques are cheap and amenable to creating any monomer in this large design space
-		\item LLCs forms lamellar, bicontinuous cubic and hexagonal phases based on solution composition
-		\item Na-GA3C11 has been described in literature as forming two types of self assembled phases - thermotropic (Colh) and lyotropic (HII)
-		\item The thermotropic, Colh, is formed by the self assembly of neat monomer
-                  %MRS2: small change below.
-		\item The lyotropic, HII phase is formed without (or in practice, with very small amounts of water)
-		\item Both assemble into cylinders with hydrophilic groups oriented inward towards the pore center and hydrophobic groups facing outward.
-The only difference is the inclusion of water in the structure which leads to minor variations in the structure with potentially different filtration properties (although no filtration experiments have been done on Colh)
-		\item Hydrophilic regions point towards pore centers
-                  %MRS2: Be more specific on ``hindered progress'' 
-		\item Until recently, they could not be aligned - hindered progress
-		\item Yale aligns them, then crosslinks them to lock in the structure - reference 2014 and 2016 papers. They say that they are scalable techniques
-		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
-		\item The Colh phase shares the same structural features with the HII phase with the exception of the presence of water.
-This paper will focus on the development of a model of the Colh phase since it is a simpler starting point and has just as much experimental data.
-The analysis used in this paper can be readily extended to the HII phase.
-	\end{itemize}
+To understand the composition of the monomer layers, we ran simulations
+created using between 4 and 8 monomers in each layer. All configurations 
+were run for at least 200 ns. We showed that we can rule out systems 
+consisting of 4, 7, and 8 monomers based purely on comparison of 
+simulated pore spacing to experimental measurements.
+(Table~\ref{table:p2p}).
 
-	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines to reduce the chemical space for design of monomers used to create separation-specific membranes.
-	\begin{itemize}
-                \item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effective water desalination and small organic separations.
-Rejection studies show that this membrane can not do desalination yet
-%MRS: ^^^nice way to turn a weakness of the materials class into an opportunity to improve them requring research! 
-		\item Colh phase studies currently limited to one monomer
-                \item Optimization efforts performed through trial and error over the past 20 years
-                \item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
-                \begin{itemize}
-                        \item What does the microscopic pore structure look like?
-			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
-			\item Is rejection of ions due to Donnan exclusion?
-                        \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
-                        \item Is water structured inside the pores, restricting low energy pathways for solutes to follow? 
-%BJC: saw something like this in a paper 
-%MRS2: good, cite if you can.
-		\end{itemize}
-		\item How can microscopic pore structure guide membrane design?
-                  \begin{itemize}
-		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
-		\item We can use molecular dynamics simulations to enhance our understanding 
-                  \end{itemize}
-	\end{itemize}
-
-	A clear picture of the nanoscopic structure of LLC membranes, gained by building 
-%MRS2: suggest ``molecular models'', as one can argue that each way of doing it is a different model, or that it might require trying 2-3 things.
-molecular models, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
-	\begin{itemize}
-%MRS2: a thought - it would be great to add what is exactly meant by ``pore walls'' and how well defined they are is not clear.
-For example, how strict is the division between the hydrophobic tails, the head groups, and the ionic groups?
-This directly affects what is meant by the ``size'' of the nanopore, and (to put somewhere else in the outline) what size exclusion means.
- 		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
-		\begin{itemize}
-			\item This could change how one thinks about molecules diffusing through membrane
-			\item Could also be a difference between lyotropic and thermotropic phases
-		\end{itemize}
-		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
-		\begin{itemize}
-			\item How do the monomer head groups pack together? Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
-			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
-			\item Substituted benzene rings exhibit an even stronger pi-stacking attraction %BJC: reference ab initio papers   	
-			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
-			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer % reference 2005-ish Zhou paper 
-		\end{itemize}
-		\item It is possible there is more than one metastable states associated with this LLC system
-		\begin{itemize}
-			\item Which phase is consistent with experiment?
-			\item Can both phases be created experimentally?
-			\item How will each state affect transport?
-		\end{itemize}
-	\end{itemize}
-
-	We must show that the developed molecular model is consistent with physical observations so that we can trust conclusions drawn about structural features characteristic of the system.
-	\begin{itemize}
-		\item This paper will illustrate the development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
-		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
-		\item We are primarily interested in reproducing the conclusions about structure which have been made from XRD experiments and ionic conductivity measurements.    
-		\item We have comparied simulated X-ray diffraction patterns to experiment in order to match major features present in the 2D patterns
-		\item We can predict ionic conductivity using two agreeing methods -- Collective diffusion and nernst einstein
-		\item We examined crosslinking mechanism and understand its influence on membrane structure
-	\end{itemize}
-
-	\section{Methods}
-
-	HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16.
-All molecular dynamics simulations were run using Gromacs version 5.1.2 and Gromacs version 2016.
-
-	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
-	\begin{itemize}
-		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
-		\item Result not global minimum but close enough for structure building
-		\item Antechamber used for atomtyping with gaff forcefield
-		\item Used Openeye Quacpac molcharge.py to assign charges
-		\item The am1bccsym method provided with Quacpac performs a conformational search and applies charges symmetrically based on the lowest energy subset of possible conformations
-		\item Anneal again 
-		\item Multiple configurations saved from annealing trajectory to prove independence of starting config. A representative structure is given in Figure ~\ref{fig:monatomistic}
-		\item Manual modifications to the structure were made to create specific geometries for X-ray diffraction experiments
-	\end{itemize}
-
-	%BJC: I'm not sure where to place this figure. ACS nano requires the methods section to go last (after conclusions). It seems like this should go earlier, but it fits the context best around here.
-	%BJC2: I think I might make this a six panel figure. The other two panels will show a cartoon and atomistic pore view.
-	\begin{figure}
-	\centering
-	\begin{subfigure}{.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:chemdraw}
-	\end{subfigure}
-	\begin{subfigure}{.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:monatomistic}
-	\end{subfigure}
-	\medskip
-	\begin{subfigure}{.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:cartoonlayer}
-	\end{subfigure}
-	\begin{subfigure}{.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:layeratomistic}
-	\end{subfigure}
-	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition how monomers might pack together %MRS2: in what way?
-(c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests a reasonable range of monomers per layer to test\label{fig:cartoonvatomistic}  
-	\end{figure}
-
-	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for a more efficient way to build the system.
-	\begin{itemize}
-          %MRS2: specify what type of self assembly -- could be that layers are faster than hexagonal pores to get to.
-	  %BJC2: Don't I suggest the type of self assembly to be assembly into the hexagonal phase? Or should I be more broad as in, we see no type of self-assembly occuring.
-		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
-		\item Attempts with Colh system not fruitful  
-		\begin{itemize}
-			\item Packed monomers into box with Packmol
-			\item Simulated for ~100 ns with no progress shown towards self assembly
-		\end{itemize}  
-		\item Wrote code to assemble monomers into Colh configuration close to what is expected 
-		\item Equilibration simulations allow structure to relax into expected configuration 
-	\end{itemize}
-
-%MRS2: need to be careful describing which stacking/layering is described where/when based on experiments actually reported.
-%BJC2: can you clarify this point?
-	Each pore is made of twenty stacked monomer layers with periodic continuity in all directions, avoiding any edge effects and creating an infinite length pore ideal for studying transport (Fig.~\ref{fig:initial})
-	\begin{itemize}
-		\item A thinner system is better to reduce the computational cost and allow us to look at longer timescales
-		\item Number of layers chosen to give sufficient resolution when simulating XRD patterns
-                \item Decided on 20 layers using a system which held a vacuum gap above and below the membrane
-                \item Too few layers leads to micelle-like formations %MRS: with gap.
-	\end{itemize}
-
-	\noindent Initial guesses for the remaining structural parameters were chosen based on experimental data and varied in order to develop a model that agrees with experiment. 
-%MRS2: ``treated as variables'' is vague. Be specific about what it means you are doing.
-	\begin{itemize}
-		\item XRD gives pore-to-pore distances of $\approx$ 4.1 nm and indicates possible pi-stacking at $\approx$ 3.7 \angstrom (see figure~\ref{fig:xrd}) on - comparison of experimental vs. simulated)
-		\item Pi-stacking exists in multiple stable configurations: sandwiched, T-shaped and parallel-displaced
-		\item T-shaped and parallel-displaced are nearly isoenergetic and more stable than the sandwiched configuration.
-		\item T-shaped configuration is most stable when benzene centers are $\approx$ 5 \angstrom apart which is not consistent with WAXS. % http://www.jbc.org/content/273/25/15458.full 
-		\item System made with stacked and parallel-displaced benzene rings to see what is favored and matches XRD
-		\item TEM images and rejection studies give a pore size estimate
-	\end{itemize}
-
-	An equilibration scheme with position restraints placed on benzene rings prevents unrealistic jumps during early equilibration steps.
-	\begin{itemize}
-		\item Equilibration scheme:
-		\begin{itemize}
-			\item Apply position restraints to monomer head groups during energy minimization 
-			\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting monomer configuration)
-			\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
-			\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate 
-		\end{itemize}
-	\end{itemize}
-
-	Using an equilibrated structure, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
-	\begin{itemize}
-		\item Crosslinking maintains alignment of cylindrical mesophases - emphasize that replicating the mechanism/kinetics is not important 
-		\item head to tail addition dominates so I only implemented that
-		\item racemic mixture - don't have to be too concerned about direction of attack 
-		\item Details of crosslinking algorithm (refer to appendix or supplemental info but give a brief overview here)
-	\end{itemize}
-
-	Simulated X-ray diffraction patterns were generated based on atomic coordinates to give a deeper understanding of the pore structure and spacing. 
-        \begin{itemize}
-               \item 3 dimensional Fourier transformed electron density generates simulated 1D and 2D diffraction patterns
-               \item The 1D patterns are generated by spherical integration of the FT
-               \item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
-               \item We matched experiment by varying the initial structure. The selection of initial structure is explained later
-        \end{itemize}
-
-	The Nernst Einstein relation and the Collective Diffusion model were both applied to the system in order to estimate ionic conductivity.
-	\begin{itemize}
-		\item There are a few ways to estimate ionic conductivity as seen in literature.
-We prefer a method which can extract an estimate based purely on an equilibrium trajectory (reference to computational electrophysiology)
-                \item We must also be sure that our analysis of results is consistent with the method used for experimental evaluation (i.e. AC impedance spectroscopy)
-                \item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system. %BJC: worth getting into? Could also just say 
-		% that we expect our calculated value to be higher since ours is perfectly aligned relative to the real system.
-                \item Two methods used to for prediction
-                \item Nernst Einstein Relation:
-                \begin{itemize}
-                        \item Widely used equation for estimating ionic conductivity
-                        \item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
-                        \item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
-                        \item Concentration is concentration of ions in the whole membrane, not just channels
-                \end{itemize}
-                \item Collective Diffusion:  %BJC: will have a very topical explanation followed by a reference to the paper from which I got the method
-                \begin{itemize}
-                        \item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
-                        \item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
-                        \item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
-                        \item A similar model has been derived and validate to predict water permeability using equilibrium simulations
-                        \item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores.
-One would expect single channel IC to be much larger than the bulk membrane %MRS: per area, since extensively, bulk would be be bigger (multiple pores)
-                \end{itemize}
-        \end{itemize}
-
-	\section{Results and Discussion}
-
-	In order to construct an initial configuration which gives reliable trends, we need to understand the composition of layers, how far apart to stack the layers, and how to orient them with respect to each other.
-
-	To understand the composition of the monomer layers, we ran simulations created with 4 - 8 monomers per layer 
-	\begin{itemize}
-		\item All configurations were stable for at least a short time %BJC: I am going to run out these simulations further and will have more to say
-                \item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Table~\ref{table:p2p})
-        \end{itemize}
-
-	The initial distance between layers is a key determining factor of the equilibrium configuration.
-	\begin{itemize}
-                \item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. 
-                \item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure.
-Benzene rings arrange in a helical conformation after equil.
-Membrane about 8 nm thick (Fig ~\ref{fig:phaseA}) % BJC: Still trying to prove that layered is trying to go towards a helical conformation.
-Also, maybe include thickness in the table?
-                \item This will be called phase A for simplicity  
-	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder, while maintaining partitioning between hydrophobic and hydrophilic regions.
-        	\begin{itemize}
-                	\item This will be called phase B (Fig~\ref{fig:phaseB})
-                	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
-                          %MRS2: below: ``Only difference''.
-Only difference is in how they are prepared.
-But presumably, there are a number of initial configurations that can lead to this one, so emphasizing that it's the only difference isn't that important.
-Also, we want to be emphasizing the thermodynamic differences, not kinetics.
-                	\item Like phase A, phase B can form at 280K. %BJC2: ^^ so get rid of this part : The only difference in simulations leading to this state, is the initial interlayer spacing
-                	\item The phase is also present when phase A is heated close to its isotropic transition point
-                	\item There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
-                	\begin{itemize}
-                        	\item Phase B has a closed pore, while phase A is open. This will impact transport mechanisms
-                        	\item Phase B membranes are thicker
-                        	\item Consequently, the pore spacing is smaller
-                	\end{itemize}
-		\end{itemize}
-                \item We have at least two metastable states
-        \end{itemize}
-
-	We varied the relative interlayer orientation between sandwiched and parallel-displaced based on our knowledge of the stability of these two pi-stacking modes.
-        \begin{itemize}
-		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a 
-%MRS2: ``clear relation'' is a bit indirect. 
-%BJC2: clear link? 
-clear link between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here %MRS2: yep, refer a figure here.
-		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
-		\item However, both configurations are stable for 100's of nanoseconds
-		\item Xray diffraction of the sandwiched configuration after equilibration shows the spots. This indicates that there is a shift towards the offset configuration.
-	\end{itemize}
-
-	The stability of crystalline phases is strongly dependent on temperature, requiring evaluation of our force field's ability to represent the temperature at which we are simulating.
-	\begin{itemize}
-		\item All of the above simulations were ran at 280K and 300K
-		\item Phase A is very stable at 280K
-		\item when bumped to 300K it is also stable, however with a larger degree of disorder %BJC: can quantify this with order parameter
-		\item We see a clear transition to Phase B for any starting configuration when the temperature is raised above 310K (~\ref{fig:transition})
-		\item Simulating the system at room temperature should be sufficient to see both phases
-                  %MRS2: what does ``sufficient'' mean here?  Sufficient for what purpose?
-	\end{itemize}
+The stability of crystalline phases is strongly dependent on temperature,
+requiring evaluation of our force field's ability to represent the 
+temperature at which we are simulating. All simulations were run and 
+equilibrated at 280K. To observe temperature dependent behavior, 
+the system temperature of 280K equilibrations were changed and the system
+was equilibrated again. Phase B is stable at all temperatures with 
+Phase A is stable at 280K. When temperature is raised to 300K, it is also
+stable, however there is a larger degree of disorder. We see a transition
+to Phase B in all cases when the temperature is raised above 310K 
+(~\ref{fig:transition}).
 
@@
 \centering
-	\begin{subfigure}
+\begin{subfigure}{0.3\textwidth}
 	\centering
@@
 \end{subfigure}
-	\begin{subfigure}
+\begin{subfigure}{0.3\textwidth}
 	\centering
@@
 	\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:phaseA}}
+	\caption{}\label{fig:phaseA}
 \end{subfigure}
@@
 	\centering
-		\caption{~\label{fig:phaseB}}
+	\caption{}\label{fig:phaseB}
 \end{subfigure}
@@
 \end{figure}
-
 %BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
 %MRS2: a little hard to say until the data is in.
+
 	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
@@
 The model gives reasonable estimates of ionic conductivity for both phases.
-	\begin{itemize}
-		\item See comparison of methods in Table~\ref{table:conductivity}
-		\item The methods agree reasonably well within error
-		\item In the future, we will probably only use Nernst Einstein because it requires less simulation to get good statistics.
-%BJC: probably don't need to mention this %MRS2: can mention it peforms better, informing future work.
-		\item Our calculated values are higher than experimental values, as expected.
-		\item The real system, although mostly aligned and straight, still has a distribution of azimuthal angles, lowering the effective ionic conductivity of the bulk membrane. 
-		\item The ordering from isotropic to mostly aligned mesophases showed an 85x increase in ionic conductivity. We would expect more gains in a perfect system.
-		\item The ordered phase has a higher calculated ionic conductivity than the disordered phase.
-	\end{itemize}
+Calculated values of ionic conductivity obtained using the Nernst Einstein
+relation and Collective Diffusion model are compared in Table~\ref{table:conductivity}.
+The two methods agree with each other within error, although the 
+uncertainty obtained using the Collective Diffusion model is much higher.
+For this reason we will likely only use the Nernst Einstein relation
+in future calculations of this type. It is evident that the ordered 
+phase has a higher ionic conductivity than the disordered phase. 
+Conductivity is enhanced in Phase A because the pores are more open,
+increasing the likelihood of site hopping. In all cases, our calculated values
+are higher than experimental values, as expected. The real system, 
+although mostly aligned and straight, still has a distribution of 
+azimuthal angles, lowering the effective ionic conductivity of the bulk 
+membrane. The ordering from isotropic to mostly aligned mesophases 
+showed an 85 fold increase in ionic conductivity. We would expect additional
+gains in a perfect system.
 
@@
 \centering
-	\begin{tabular}{|c|c|}
+\begin{tabular}{ccc}
+\toprule
+\multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
 \hline
-	Nernst Einstein & Collective Diffusion \\
-	\hline
+Method & Phase A & Phase B \\
+\midrule
+Nernst Einstein & \num{8e-5} & \num{8e-5} \\
+Collective Diffusion & \num{6e-5} & \num{6e-5} \\
+Experiment & \num{1.3e-5} & \num{1.3e-5} \\
+\bottomrule
 \end{tabular}
@@
 Using the design framework and analysis methods applied herin, we have the ability to reliably predict structures of new nanoporous membranes.
-
-	\section{Conclusion}
-
-	In this work, we have suggested a more detailed picture of the structure of a self assembled thermotropic liquid crystal membrane using an atomistic molecular model.
-	\begin{itemize}
-		\item The model's physical properties are consistent with experimental measurements
-                  %MRS2: are these two disordered and offset?  If so, then one is stable (Though we are not sure at 300K which is which).  Or are you referring to three phases?
-		\item We have discovered the existence of two metastable configurations that persist at room temperature
-		\item This methodology has been developed for a specific case but can be readily adapted to other LLCs
-	\end{itemize}
-	%MRS: focus around what we learned about the system - not that we have a model
-
-	\section{Supplemental Information} %MRS2: check, might be called supporting information, depending on the journal. %BJC2: Also, it's a separate document in ACS nano at least
-
-	Monomer configurations
-	\begin{itemize}
-		\item Pore-to-pore equilibration plots
-		\item Plots of other things that level off indicating equilibration
-		\item 3D visualizations of different configurations tested
-		\item Sodium ion distribution in disordered phase
-	\end{itemize}
-
-        \begin{figure}
-		\centering
-		\includegraphics{placeholder.png}
-                \caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
-                %MRS2: what is the thesis?
-                \label{fig:initial}
-        \end{figure}
-
-	Equilibration procedure
-
-	\noindent Crosslinking details
-	\begin{itemize}
-		\item Algorithm description. Link to full algorithm in git repository
-		\item A figure showing the new crosslinks
-	\end{itemize}
-
-	\noindent Ionic conductivity % plus more details on implementation.
-	\begin{itemize}
-		\item MSD plots
-	\end{itemize}
-\end{document}

### 2017-07-27 Ben_Manuscripts/Paper1/intro.tex
Update intro.tex

@@
 because they offer the ability to control membrane architecture at the
-atomic scale allowing design of solute-specific separation membranes 
+atomic scale allowing the design of solute-specific separation membranes 
 \cite{humplik_nanostructured_2011}. Most membrane-based aqueous 
@@
 \cite{bowen_modelling_2002}.
+% Thesis: RO and NF are imperfect
+% RO membranes are tortuous and polydisperse, energy intensive, can't do targeted separations well
+% NF lower energy but has a pore size distribution
 
 Nanostructured membranes can bypass many of the performance issues which
-plague traditional NF and RO membranes. Targeted separations can be 
-accomplished by tuning size and functionality of the molecular building
-blocks which form these materials. Solute rejecting pore sizes can be
+plague traditional NF and RO membranes. One can accomplish targeted
+separations by tuning size and functionality of the molecular building
+blocks which form these materials. Solute rejecting pore sizes can be  % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
 tuned uniformly, resulting in sharp size cut-offs. Entirely different
@@
 material which can inspire novel separation techniques.
+% Thesis: Nanostructured materials can overcome issues seen in RO and NF
+% We can achieve targeted separations by controlling the system arhitecture
+% We can get uniform pore sizes 
+% we can create new separation techniques by learning about these systems <-- This point might be better elsewhere
 
@@
 defects formed during membrane synthesis \cite{li_desalination_2004}.
+% Thesis: Past development has been limited by the ability to create working membranes at a useful scale	  
+% Graphene sheets have defects
+% Carbon nanotubes can't be made uniform or aligned
+% Zeolites may have interstitial defects hurting performance
 
-Self assembling lyotropic liquid crystals (LLCs) share the characteristic
+Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate
+for aqueous separation applications. They share the characteristic
 ability of nanostructured membrane materials to create highly ordered 
@@
 phase. In both cases, monomers assemble into mesophases made of 
-hexagonally packed cylinders with hydrophilic groups oriented inward
+hexagonally packed, uniform size, cylinders with hydrophilic groups oriented inward
 towards the pore center and hydrophobic groups facing outward. Until
@@
 \cite{feng_thin_2016}. Following this breakthrough, research into LLC
-membranes has been reinvigorated. This paper will focus on 
-the development of a model of the Col\textsubscript{h} phase membrane
-meant to accelerate development of LLC membranes. We have chosen to 
-model the Col\textsubscript{h} phase since it is a simpler starting 
-point and has just as much experimental structural data as the 
-H\textsubscript{II} phase.
+membranes has been reinvigorated. We have chosen to focus our efforts 
+on the development of a model of the Col\textsubscript{h} phase membrane
+in order to accelerate development of LLC membranes.  Compared to the 
+H\textsubscript{II} phase, the Col\textsubscript{h} phase is a simpler
+starting point, due to the absence of water, and has equivalent 
+experimental structural data. 
+. 
+% Thesis: LLCs would make good filtration membranes
+% They share the same properties as other nanostructured materials
+% They can be scaled and are cheap to make
+% LLCs have a large chemical design space
+% It has been studied extensively
+% Ordered - hexagonally packed cylinders with uniform sized pore regions
+% Scalable - alignment gets rid of some performance issues associated with misalignment
 
@@
 A molecular level understanding of LLC membrane structure will elucidate
-small molecule transport mechanisms, providing guidelines to reduce the
-chemical space for design of monomers used to create separation-specific
+small molecule transport mechanisms, providing guidelines for reducing the
+chemical space for the design of monomers used to create separation-specific
 membranes. We do not yet understand how to reduce the effective pore
-size or tune the chemical environment in the H\textsubscript{II} 
+size or how to tune the chemical environment in the H\textsubscript{II} 
 nanopores for effective water desalination and small organic separations.
@@
 modifications\cite{resel_structural_2000}. Optimization has been 
-performed through trial and error. The only source of predictive modeling
+performed through trial and error. The only source of predictive modeling  % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
 has been macroscopic models which likely do not adequately describe 
@@
 detailed picture of the nanoscopic pore structure. Pore components may 
-play a role in rejection of charged or uncharged solutes. Choice of 
-counterion may influence the establishment of a donnan potential
+play a role in the rejection of charged or uncharged solutes. Choice of 
+counterion may influence the establishment of a Donnan potential
 affecting the degree to which the membrane can exclude charged species.
@@
 future membranes. 
+%Thesis: A molecular model will help us understand solute transport in these
+% systems and aid in the selection of monomers for creating new membranes
+% We can figure out a way to make desalination feasible
+% Most attempts at improvement have been based on trial and error
+% Past modeling hasn't been nanoscopically detailed and can't tell us what
+% we need to know to make improved membranes 
+% An atomistic model can actually help direct design
 
-%BJC: I dont like this sentence vvv
+%BJC: Can't decide which thesis to use
+% Thesis 1
 A clear picture of the nanoscopic structure of LLC membranes, gained by
-building a molecular model, will provide evidence to support or call
+building a molecular model will provide evidence to support or call
 into question past drawn conclusions that have largely guided our 
-understanding of separation mechanisms.	The arrangement of sodium ions
+understanding of the system. 
+% Thesis 2
+A clear picture of the nanoscopic LLC membrane structure, gained by building 
+a molecular model will provide evidence to answer existing and newly proposed
+questions.
+The arrangement of sodium ions
 in the channels is thought to be confined to the pore walls. It is 
@@
 based on the volume of the liquid crystal monomers proposes that there 
-are seven monomers in each layer~\cite{resel_structural_2000}. Once we 
+are seven monomers in each layer~\cite{resel_structural_2000}.
+Once we %BJC: why is knowing the number of monomers in each layer important to experimentalists at all - find monomers which prefer to pack more densely - high ionic conductivity?
 know the number of monomers in each layer, we still do not know how 
@@
 assembly in this system is thought to be pi-stacking interactions
-between headgroup benzene rings\cite{gazit_possible_2002}. Gas phase ab
+between aromatic headgroups\cite{gazit_possible_2002}. Gas phase ab
 initio studies of benzene dimers have shown a clear energetic advantage
@@
 %BJC: might get rid of this last point since we don't address experimental viability of metastable states
+%BJC2: well let's see what results Xunda can pull out
 be produced experimentally and what implications each state might have
 regarding transport properties.
+% Thesis: Knowing what the molecular structure can validate and explain work that has been done in the past
+% We might construct a different picture of the arrangement of sodium ions 
+% We might be able to answer how many monomers are in each layer
+% How do benzene rings stack on top of each other?
+% Is it possible there are more metastable states?
 
 We must show that the developed molecular model is consistent with
-physical observations so that we can trust conclusions drawn about 
-structural features characteristic of the system. This paper will
+physical observations so that we can trust conclusions drawn about % better word for trust?
+structural features characteristic of the system. This article will
 illustrate the development of a predictive molecular model and the steps
@@
 2D patterns. We calculate ionic conductivity using two agreeing methods.
-We examined the crosslinking mechanism and understand its influence on
+We examined the the influence of crosslinking on
 membrane structure. The analysis used in this paper can be readily
-extended to the H\textsubscript{II} phase.
+extended to the H\textsubscript{II} phase and other similar LC systems.
+% Thesis: Our model needs to be consistent with experimental observations
+% A bunch of things we can compare to

### 2017-07-31 Ben_Manuscripts/Paper1/methods.tex
revisions

@@
 shipped with Openeye Scientific software's QUACPAC. Using the new
-charges, the monomer system was annealed again and multiple monomer
+charges, the monomer system was annealed again and monomer
 configurations were pulled from the trajectory to be used for full
@@
 
-Each pore consists of twenty stacked monomer layers with periodic 
-continuity in all directions, avoiding any edge effects and creating an
-infinite length pore ideal for studying transport. A small number of
-layers is preferred in order to reduce computational cost and to allow
-us look at longer timescales. Ultimately, we chose to build a system
+A typical simulation volume contains four pores in a monoclinic unit cell,
+the smallest unit cell that maintains hexagonal symmetry when extended 
+periodically. Each pore is made of twenty stacked monomer layers with
+% describe unit cell in terms of alpha beta gamma angles?
+% mention semi-isotropic pressure coupling here or later
+periodic continuity in all directions, avoiding any edge effects and 
+creating an infinite length pore ideal for studying transport. A small
+number of layers is preferred in order to reduce computational cost and 
+to allow us to look at longer timescales. Ultimately, we chose to build a system
 with 20 layers of monomer in each pore in order to give sufficient

### 2017-08-07 Ben_Manuscripts/Paper1/methods.tex
revisions

@@
 dynamics simulations were run using Gromacs version 5.1.2 and Gromacs 
-version 2016. \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,
+version 2016. \cite{bekker_gromacs:_1993,berendse n_gromacs:_1995,
 van_der_spoel_gromacs:_2005,hess_gromacs_2008}
+% Software used
 
@@
 system construction.
+% monomer parametrization
 
@@
 using Packmol\cite{martinez_packmol:_2009}. Simulations of $>$ 100 ns 
-show no progress towards an ordered system. To bypass the slow self-assembly
-process, python code was written that assembles monomers into a structure 
-close to the expected equilibrium configuration. A short, restrained 
-equilibration, followed by NPT simulations $>$ 500 ns, allows the initial
-configuration to relax into an equilibrium configuration. Our logic for
-choosing a starting configuration and the details of the equilibration 
-schemes are presented below.
+show no indicators of progress towards an ordered system. To bypass the
+slow self-assembly process, python scripts are used to assemble 
+monomers into a structure close to the expected equilibrium configuration.
+A short, restrained equilibration, followed by NPT simulations $>$ 500 ns, 
+allows the initial configuration to relax into an equilibrium configuration.
+Our logic for choosing a starting configuration and the details of the equilibration 
+schemes are presented below. % eliminate this sentence?
+% Unit Cell building method and justification
 
@@
 to allow us to look at longer timescales. Ultimately, we chose to build a system
-with 20 layers of monomer in each pore in order to give sufficient
-resolution when simulating X-ray diffraction patterns.
+with 20 monomer layers each pore in order to give sufficient
+resolution when simulating X-ray diffraction patterns.  % BJC: reword / mention xrd resolution - system size dependence in previous sentence
 
@@
 spacing was chosen to be 10 \% larger than the experimental value. 
-The layer spacing was based on reflections from experimental 2D WAXS
-data at 3.7 \angstrom, thought to represent pi-stacking between stacked
-benzene rings\cite{feng_scalable_2014}. The tendency of simulations to
-equilibrate to slightly larger interlayer spacing inspired systems
-starting with layer spacings $>$ 4 \angstrom.
+The layer spacing was based on experimental 2D WAXS data which shows
+reflections corresponding to features spaced 3.7 \angstrom apart. It has 
+been hypothesized that the features are present due to pi-pi
+interactions between stacked aromatic rings\cite{feng_scalable_2014}. 
+Our simulations tend to equilibrate to a wider interlayer spacing of \approx 4.1 \angstrom,
+which inspired separate systems starting with layer spacings $>$ 4 \angstrom.
+Initial pore radius estimates were based on past TEM 
+images and size exclusion rejection data\cite{feng_scalable_2014,
+feng_thin_2016,zhou_supported_2005}.
 % There is plenty I can say about initial configuration. Starting layers
 % too far apart, too close, tilted initial configurations etc.
-The relative interlayer orientation was chosen based on the various 
-stacking modes of benzene and substituted benzene rings: sandwiched,
-T-shaped and parallel-displaced. The T-shaped configuration was ruled
-out based on the inconsistency of its preferred stacking distance of 
-$\approx$ 5 \angstrom, with diffraction data. The system's preference
+The relative interlayer orientation was chosen based on clues from diffraction
+data as well as the various known stacking modes of benzene and substituted 
+benzene rings: sandwiched, T-shaped and parallel-displaced. The T-shaped configuration was ruled
+% BJC: Figure showing benzene pi-stacking modes and 
+out based on the inconsistency of its $\approx$ 5 \angstrom equilibrium 
+stacking distance with diffraction data. The system's preference
 towards the sandwiched vs. parallel displaced stacking modes was left
-as a variable. Initial pore radius estimates were based on past TEM 
-images and size exclusion rejection data\cite{feng_scalable_2014,
-feng_thin_2016,zhou_supported_2005}.
+to be explored. Visualization of each configuration suggests entropic differences 
+based on the way the tails are able to pack. This difference may 
+explain, in part, which stacking mode is more favorable.
 
-An equilibration scheme with position restraints placed on benzene rings
+An equilibration scheme with position restraints placed on aromatic rings
 prevents unrealistic jumps during early equilibration steps. Restraints
-allow the monomer head groups to remain in the sandwiched or parallel-displaced 
-configurations while monomer tails settle. Doing so also helps prevent
-system dependence on initial monomer configuration. During the restrained
-equilibration, force constants are reduced by the square root of the 
-previous force constant every 50 ps, with a starting value of 1e6 KJ
-mol\textsuperscript{-1} nm\textsuperscript{-2}. Once the force constant
+fix monomer head groups in the sandwiched or parallel-displaced 
+configurations while allowing monomer tails to settle. Doing so also mitigates 
+system dependence on initial monomer configuration. Restrained
+equilibrations are run in the NVT ensemble. Every 50 ps, force constants 
+are reduced by the square root of its previous value, starting from 
+1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}. Once the force constant
 is below 10 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}, the 
-restraints are slowly released until there is no more restriaining 
-potential. All restrained equilibrations are run in the NVT ensemble. 
-The resulting unrestrained structure is subsequently allowed to 
-equilibrate in the NPT ensemble for $>$ 200 ns.
+restraints are slowly released until there is no more restraining 
+potential. The resulting unrestrained structure is allowed to 
+equilibrate in the NPT ensemble for $>$ 200 ns.  % should probably run all of them to x ns rather than making it ambiguous
 
@@
 constant under a range of simulation conditions (see supplemental info). 
+% BJC: This paragraph could be shortened and some of it put in the supplemental info, but I like it here for now
 
@@
 initial structure and equilibration procedure 
+% Replace with a description written by Joe
 
@@
 $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$ Sodium ion diffusion 
-coefficients were found by calculating the slope of mean square
-displacement curve as indicated by the einstein relation
+coefficients were found by calculating the slope of the linear
+region of the mean square displacement curve as indicated by the einstein relation
 \cite{einstein_investigations_1956}. Ion concentration was measured with
@@
 derivation of the model can be accessed elsewhere\cite{liu_collective_2013}.  
+% Talk about error somewhere?

### 2017-08-07 Ben_Manuscripts/Paper1/results.tex
Update results.tex

@@
 
+% Paragraph describing the experimental 2D WAXS Pattern
+
 Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
@@
 parallel-displaced based on our knowledge of the stability of these two
-pi-stacking modes. Short simulations were run with position restraints
-on benzene rings. Simulated X-ray diffraction patterns generated from 
-each configuration establishes a link between the parallel displaced 
-stacking mode and major features present in experimental XRD patterns.  % FIGURE!!!!!!!!!!
-The faint ring at a distance of $\approx$ 1.5 \angstrom \textsuperscript{-1} 
-is commonly identified as a result of the average packing distance 
-between alkane chains. Four spots of higher intensity are visible in the 
-alkane chain region creating an x-shaped pattern. The spots are only
+pi-stacking modes. Short NVT simulations were run with position restraints
+on aromatic ring carbon atoms. Simulated X-ray diffraction patterns 
+generated from each configuration establishes a difference between the two
+stacking modes. In each pattern, a faint ring is present at a distance of
+$\approx$ 1.5 \angstrom \textsuperscript{-1} which is commonly identified
+as the result of the average packing distance between alkane chains. 
+The parallel displaced configuration contains two lines of high intensity.
+The lines have the highest intensity where they intersect the alkane chain region
+due to constructive interference between the two features. The lines are located 
+at a qz value of 0.76 \angstrom \textsuperscript{-1}, half the qz value corresponding
+to layer stacking. This is significant because the same relative spacing between 
+reflections is present in the expermental WAXS pattern between the pi-pi stacking
+reflections at qz = 1.7 \angstrom \textsuperscript{-1} and the reflection attributed
+to 2_1 helical ordering at qz = 0.85 \angstrom \textsuperscript{-1}. As the 
+simulation is progressed, the full line begins to fade and the high intensity
+persists only at the intersection with the alkane chain ring. Most significantly, 
+the line is no longer present at r = 0. It is possible
+
 generated for structures created in the parallel displaced configuration.

### 2017-08-07 Ben_Manuscripts/Paper1/results.tex
revisions

--- 2017-06-21 Ben_Manuscripts/Paper1/results.tex
@@
 
+% Paragraph describing the experimental 2D WAXS Pattern
+The experimental 2D WAXS measurement contains five major reflections which
+our model intends to reproduce (Fig ~\ref{fig:WAXSexp}). The first is located
+at qz = 1.7 \angstrom \textsuperscript{-1}, corresponding to a real space 
+spacing of 3.7 \angstrom. The reflection is attributed to pi-pi stacking
+between aromatic rings in the direction perpendicular to the membrane plane, or z-axis. 
+For simplicity, this reflection will be referred to as R-pi. A weak intensity
+line is located at exactly half the qz value of R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
+real space periodic spacing of 7.4 \angstroms. This reflection has been 
+attributed to 2\textsubscript{1} helical ordering of aromatic rings along the
+z axis and will therefore be referred to as R-helix. If positions of the 
+aromatic rings can be traced by a helix, then for each turn in the helix, 
+there should be two aromatic rings. A third major reflection is marked by 
+a low intensity ring located at r = 1.4 \angstrom \textsuperscript{-1}. The
+real space separation corresponds to 4.5 \angstroms which is characteristic
+of the average spacing between packed alkane chains. This reflection will be
+called R-alkanes. Within R-alkanes, are four spots of higher intensity which 
+will be called R-spots. All are located \approx 40 degrees from the qz axis
+in their respective quadrants. In many liquid crystal systems this can be
+attributed to the tilt angle of the alkane chains with respect to the xy axis. 
+The final major reflections correspond to the spacing and symmetry of the d100 
+plane which can be related to the distance between pores. The feature is
+characterized by dots along qz = 0. The spacing between dots is indicative
+of the hexagonal symmetry of the packed pores. It is easiest to interpret 
+the data by radially integrating the 2D data to get a 1D curve which has
+also been done.
+
 Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
@@
 parallel-displaced based on our knowledge of the stability of these two
-pi-stacking modes. Short simulations were run with position restraints
-on benzene rings. Simulated X-ray diffraction patterns generated from 
-each configuration establishes a link between the parallel displaced 
-stacking mode and major features present in experimental XRD patterns.  % FIGURE!!!!!!!!!!
-The faint ring at a distance of $\approx$ 1.5 \angstrom \textsuperscript{-1} 
-is commonly identified as a result of the average packing distance 
-between alkane chains. Four spots of higher intensity are visible in the 
-alkane chain region creating an x-shaped pattern. The spots are only
+pi-stacking modes. Short NVT simulations were run with position restraints
+on aromatic ring carbon atoms. Simulated X-ray diffraction patterns 
+generated from each configuration establish a difference between the two
+stacking modes. In each pattern, R-alkanes is present at a distance of
+$\approx$ 1.5 \angstrom \textsuperscript{-1}. R-pi is also present in each 
+pattern, although it appears to intersect R-alkanes because the spacing
+between aromatic rings is similar to the alkane chain packing. The difference 
+in aromatic ring spacing between experiment and simulation is likely a result
+of the inability of GAFF to properly handle pi interactions. The parallel
+displaced configuration contains two lines of high intensity with maximum
+intensity occurring where they intersect the alkane chain region due to
+constructive interference between the two features. The lines are located
+where one would expect to see R-helix. As the simulation is progressed, 
+the full line begins to fade and the reflection persists only at the 
+intersection with the R-alkanes. Most significantly, the line is no
+longer present where R-helix exists and, perhaps coincidentally, the 
+intersection with R-alkanes occurs where one would expect to see R-spots.
+
 generated for structures created in the parallel displaced configuration.
@@
 
-Further simulation indicates that both configurations are stable for 
-100's of nanoseconds. Simulated diffraction of the sandwiched 
-configuration after equilibration shows the spots which were not initially
+Applying our full equilibration scheme results in structures which indicate
+that both configurations are stable for 100's of nanoseconds. Simulated 
+diffraction of the sandwiched configuration after equilibration shows the spots which were not initially
 present, implying that there is a shift towards the parallel-displaced

### 2017-08-15 Ben_Manuscripts/Masters_Bypass/master.tex
A separate folder for my Master's Bypass paper

\documentclass[journal=ancac3]{achemso}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\newcommand{\angstrom}{\textup{\AA}}

\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations}
\author{Benjamin J. Coscia}
\email{benjamin.coscia@colorado.edu}
\author{Douglas L. Gin}
\author{Richard D. Noble}
\author{Michael R. Shirts}
\affiliation{University of Colorado, Boulder, Colorado 80309, United States}

\begin{document}

\graphicspath{{./figures/}}  % put all the figures here
\maketitle

\include{intro}
\include{results}
\include{conclusion}
\include{methods}
%\include{supp} supplementary info should be included as a separate document for ACSnano

\newpage
\bibliography{llc.bib}
\end{document}

### 2017-08-15 Ben_Manuscripts/Masters_Bypass/results.tex
Outline converted to paragraphs

--- 2017-08-07 Ben_Manuscripts/Paper1/results.tex
@@
 to stack the layers, and how to orient them with respect to each other.
+To verify our choices for each parameter, we compare our calculations
+to experimental small angle X-ray scattering (SAXS), wide angle X-ray
+scattering (WAXS), and ionic conductivity measurements.
 
-The initial distance between layers can influence the approach towards
-equilibrium. In the real system, according to wide angle X-ray
-scattering (WAXS) experiments, layers are stacked 3.7 \angstrom apart.
-A characteristic of equilibrated systems simulated in this way, is a
-defined, cylindrical and open pore structure. Benzene rings arrange in
-a helical conformation after equilbration. The membrane is about 8 nm
-thick. We will refer to this system as Phase A. (Fig ~\ref{fig:phaseA})
-Simulations of systems built with layers stacked > 4 \angstrom apart
-results in a pore structure characterized by high radial disorder,
-while maintaining partitioning between hydrophobic and hydrophilic
-regions. This will be called phase B (Fig~\ref{fig:phaseB})
-% The arrangement of sodium ions (which are closely bound to carbonyl
-% head groups) can be well-approximated by a gaussian distribution 
-It is apparent that this LLC membrane may exist in at least two
-metastable states. The distinct difference in pore structure exhibited
-by each phase will likely lead to different transport mechanisms.
-Understanding which phase exists experimentally is necessary in order
-to appropriately study the system.
-%Like phase A, phase B can form at 280K. 
-%The phase is also present when phase A is heated close to its isotropic transition point
-%There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
+To understand the composition of the monomer layers, we ran simulations of 
+systems created with 4 - 8 monomers per layer. Both the sandwiched and 
+parallel displaced configurations were tested. All systems remained
+stable for at least 50 ns. Pair correlation functions calculated between 
+aromatic rings along the length of the pores indicate that systems prefer to
+stay partitioned into layers (Fig~\ref{fig:zdf}). Pore spacings were 
+calculated by measuring the distance between the pore centers. Pore centers
+were located by averaging the coordinates of sodium ions in their 
+respective pores. Statistics were generated using the bootstrapping 
+technique. Systems built with 5 monomers in each layer equilibrate to a pore
+spacing that is most consistent with the experimental value of 4.12 nm
+derived from SAXS measurements (Table~\ref{table:p2p}). The remainder of
+this discussion will focus on the analysis of systems built with 5 
+monomers per layer.
 
-% Paragraph describing the experimental 2D WAXS Pattern
 The experimental 2D WAXS measurement contains five major reflections which
@@
 The final major reflections correspond to the spacing and symmetry of the d100 
-plane which can be related to the distance between pores. The feature is
-characterized by dots along qz = 0. The spacing between dots is indicative
-of the hexagonal symmetry of the packed pores. It is easiest to interpret 
-the data by radially integrating the 2D data to get a 1D curve which has
-also been done.
+plane which can be related to the distance between pores. The feature, which 
+will be called R-pores, is characterized by dots along qz = 0. The spacing
+between dots is indicative of the hexagonal symmetry of the packed pores. It
+is easiest to interpret the data by radially integrating the 2D data to get 
+a 1D curve which has also been done.
 
-Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
-        \begin{itemize}
-                \item Phase A
-                \begin{itemize}
-                        \item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
-                        \item There is evidence that the stacked configuration will shift towards an offset configuration over time.
-WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
-                        \item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
-                        \item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
-                \end{itemize}
-                \item Phase B
-                \begin{itemize}
-                        \item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
-                        \item No spots at all which is consistent with the disorder shown by the rings in the pore
-                \end{itemize}
-                \item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom \textsuperscript{-1} which is typical of packed alkane chains
-                \item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B,
-%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
-they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present
-%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
-%BJC2: Are you thinking about the fourier transforms? I could bring that in
-        \end{itemize}
+The initial distance between layers can influence the approach towards
+equilibrium. Equilibrated systems built according to the 3.7 \angstrom
+spacing indicated by R-pi are characterized by a defined, cylindrical and
+open pore structure. Aromatic rings are arranged in a helical conformation.
+We will refer to this system as Basin A (Fig ~\ref{fig:phaseA}). Simulations
+of systems built with layers stacked > 4 \angstrom apart results in a pore
+structure characterized by high radial disorder, while still maintaining 
+partitioning between hydrophobic and hydrophilic regions. This will be 
+called Basin B (Fig~\ref{fig:phaseB}). It is apparent that this LLC membrane
+may exist in at least two metastable states. The distinct difference in 
+pore structure (Fig~\ref{fig:porestructures}) exhibited by each phase will
+likely lead to different transport mechanisms. Understanding which phase 
+exists experimentally is necessary in order to appropriately study the system.
+% BJC: include more examples of the difference between the two basins
+% The arrangement of sodium ions (which are closely bound to carbonyl
+% head groups) can be well-approximated by a gaussian distribution 
+% Like phase A, phase B can form at 280K. 
+% The phase is also present when phase A is heated close to its isotropic transition point
+% There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
 
@@
 
-generated for structures created in the parallel displaced configuration.
-In the past, the spots have been attributed to the tilt angle of the 
-alkane chains. Theoretically the angle is the same as that made between 
-the spots and the x-axis. However, we achieved the same pattern with 
-a calculated average tilt angle of 0 $\pm$ 9 degrees. % GET THE RIGHT NUMBER !!!!!
+Full comparison of experimental 2D WAXS with simulated X-ray diffraction
+patterns produced from equilibrated MD trajectories shows the most consistency
+with the sandwiched conformation in Basin A. Systems were built in both the 
+parallel displaced and sandwiched conformations with an intial layer spacing of
+3.7 \angstrom. A third system was created by stacking layers in the sandwiched 
+conformation 5 \angstrom apart in order to guide it towards Basin B. For ease of
+reference, the third system will be referred to as the disordered system. The 
+three systems were equilibrated according to our procedure with NPT simulations of 
+greater than 400 ns. Simulated diffration patterns were generated using 
+portions of the trajectory after equilibration. Equilibration was detected
+when the distance between pores and the membrane thickness stopped changing.
+Simulated diffraction patterns for all three structures are shown in 
+Fig~\ref{fig:XRDsim}. The equilibrated parallel displaced structure exhibits 
+R-alkanes and R-pores in the expected locations. Due to low resolution, making
+out the individual spots of R-pores is challenging and can be validated upon
+further inspection of the 3D structure factor. R-pi is also present, however it
+intersects R-alkanes because it is at a lower q than expected. This can be 
+explained by our model's inability to appropriately represent aromatic interactions.
+The rings prefer to stack \approx 4.1 \angstrom apart as opposed to 3.7 \angstrom.
+R-helix and R-spots are both missing. The line which intersected both of these
+features in the restrained simulations faded upon equilibration which suggests
+that monomers in the parallel-displaced conformation may not give rise to the 
+experimental WAXS pattern seen. Simulated XRD of the sandwiched configuration 
+contains all features except for R-helix. Most notably, R-spots appears in the
+expected location, which suggests that there is something intrinsically to
+the sandwiched packing which gives rise to such features. Finally, the 
+disordered structure exhibits R-alkanes and R-pores. R-helix are R-spots are not
+present. Given the evidence, the sandwiched configuration with layers spaced
+3.7 \angstrom apart gives rise to an equilibrated structure closest to experiment.
 
-Applying our full equilibration scheme results in structures which indicate
-that both configurations are stable for 100's of nanoseconds. Simulated 
-diffraction of the sandwiched configuration after equilibration shows the spots which were not initially
-present, implying that there is a shift towards the parallel-displaced
-mode. To quantify the degree of sandwiched stacking, we measured the 
-amount of overlap between projections of benzene rings and those below
-them. The amount of overlap between projections decreases rapidly. % FIGURE !!! overlap
-
-To understand the composition of the monomer layers, we ran simulations
-created using between 4 and 8 monomers in each layer. All configurations 
-were run for at least 200 ns. We showed that we can rule out systems 
-consisting of 4, 7, and 8 monomers based purely on comparison of 
-simulated pore spacing to experimental measurements.
-(Table~\ref{table:p2p}).
-
-The stability of crystalline phases is strongly dependent on temperature,
-requiring evaluation of our force field's ability to represent the 
-temperature at which we are simulating. All simulations were run and 
-equilibrated at 280K. To observe temperature dependent behavior, 
-the system temperature of 280K equilibrations were changed and the system
-was equilibrated again. Phase B is stable at all temperatures with 
-Phase A is stable at 280K. When temperature is raised to 300K, it is also
-stable, however there is a larger degree of disorder. We see a transition
-to Phase B in all cases when the temperature is raised above 310K 
-(~\ref{fig:transition}).
+The spots that appear in the simulated XRD pattern of the sandwiched
+conformation are a result of the way alkane tails pack together. Previously,
+the spots in the diffraction pattern had been explained as the product of
+tilted alkane chains. We measured the tilt angle of the alkane chains and 
+showed that our system equilibrates to an average tilt angle close to zero 
+degrees (Fig~\ref{fig:tilt}). To understand the origin of the spots, we 
+determined which atoms gave rise to the feature. By removing atoms from 
+the trajectory and simulating a diffraction pattern, we were able to isolate
+the cause of the spots to the tails. Since the tails are mostly flat, we
+plotted the centroids of the tails and measured the angle between each centroid 
+and its nearest neighbors with respect to the plane of the membrane. The 
+distribution of these angles is consistent with the location of the spots.
+We reason that monomer tails stacked closely in the sandwiched conformation
+are forced to splay apart and pack in between in each other which creates a
+nearly hexagonal array of packed tails.
 
@@
 	\end{subfigure}
-\caption{(a) As temperature is increased, Phase A transitions to Phase B, becoming more disordered.
+	\caption{(a) As temperature is increased, Phase A transitions to 
+	Basin B, becoming more disordered.
 An order parameter of 1 indicates perfect ordering, while 0 indicates disorder.
@@
 %MRS2: a little hard to say until the data is in.
-
-	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
-	\begin{itemize}
-		\item Phase A
-		\begin{itemize}	
-			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
-			\item There is evidence that the stacked configuration will shift towards an offset configuration over time.
-WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
-			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
-			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
-		\end{itemize}
-		\item Phase B
-		\begin{itemize}
-			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
-			\item No spots at all which is consistent with the disorder shown by the rings in the pore
-		\end{itemize}
-		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\textsuperscript{-1} which is typical of packed alkane chains
-		\item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B, 
-%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
-they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present   
-%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
-%BJC2: Are you thinking about the fourier transforms? I could bring that in
-	\end{itemize}
 
@@
 	\end{table}
-
-	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies.
-Using the design framework and analysis methods applied herin, we have the ability to reliably predict structures of new nanoporous membranes.

### 2017-08-15 Ben_Manuscripts/Masters_Bypass/conclusion.tex
Create conclusion.tex

--- 2017-06-21 Ben_Manuscripts/Paper1/results.tex
@@
-\section{Results and Discussion}
-
-In order to construct an initial configuration which gives reliable 
-trends, we need to understand the composition of layers, how far apart
-to stack the layers, and how to orient them with respect to each other.
-
-The initial distance between layers can influence the approach towards
-equilibrium. In the real system, according to wide angle X-ray
-scattering (WAXS) experiments, layers are stacked 3.7 \angstrom apart.
-A characteristic of equilibrated systems simulated in this way, is a
-defined, cylindrical and open pore structure. Benzene rings arrange in
-a helical conformation after equilbration. The membrane is about 8 nm
-thick. We will refer to this system as Phase A. (Fig ~\ref{fig:phaseA})
-Simulations of systems built with layers stacked > 4 \angstrom apart
-results in a pore structure characterized by high radial disorder,
-while maintaining partitioning between hydrophobic and hydrophilic
-regions. This will be called phase B (Fig~\ref{fig:phaseB})
-% The arrangement of sodium ions (which are closely bound to carbonyl
-% head groups) can be well-approximated by a gaussian distribution 
-It is apparent that this LLC membrane may exist in at least two
-metastable states. The distinct difference in pore structure exhibited
-by each phase will likely lead to different transport mechanisms.
-Understanding which phase exists experimentally is necessary in order
-to appropriately study the system.
-%Like phase A, phase B can form at 280K. 
-%The phase is also present when phase A is heated close to its isotropic transition point
-%There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
-
-        Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
-        \begin{itemize}
-                \item Phase A
-                \begin{itemize}
-                        \item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
-                        \item There is evidence that the stacked configuration will shift towards an offset configuration over time.
-WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
-                        \item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
-                        \item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
-                \end{itemize}
-                \item Phase B
-                \begin{itemize}
-                        \item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
-                        \item No spots at all which is consistent with the disorder shown by the rings in the pore
-                \end{itemize}
-                \item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom \textsuperscript{-1} which is typical of packed alkane chains
-                \item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B,
-%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
-they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present
-%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
-%BJC2: Are you thinking about the fourier transforms? I could bring that in
-        \end{itemize}
-
-We varied the relative interlayer orientation between sandwiched and 
-parallel-displaced based on our knowledge of the stability of these two
-pi-stacking modes. Short simulations were run with position restraints
-on benzene rings. Simulated X-ray diffraction patterns generated from 
-each configuration establishes a link between the parallel displaced 
-stacking mode and major features present in experimental XRD patterns.  % FIGURE!!!!!!!!!!
-The faint ring at a distance of $\approx$ 1.5 \angstrom \textsuperscript{-1} 
-is commonly identified as a result of the average packing distance 
-between alkane chains. Four spots of higher intensity are visible in the 
-alkane chain region creating an x-shaped pattern. The spots are only
-generated for structures created in the parallel displaced configuration.
-In the past, the spots have been attributed to the tilt angle of the 
-alkane chains. Theoretically the angle is the same as that made between 
-the spots and the x-axis. However, we achieved the same pattern with 
-a calculated average tilt angle of 0 $\pm$ 9 degrees. % GET THE RIGHT NUMBER !!!!!
-
-Further simulation indicates that both configurations are stable for 
-100's of nanoseconds. Simulated diffraction of the sandwiched 
-configuration after equilibration shows the spots which were not initially
-present, implying that there is a shift towards the parallel-displaced
-mode. To quantify the degree of sandwiched stacking, we measured the 
-amount of overlap between projections of benzene rings and those below
-them. The amount of overlap between projections decreases rapidly. % FIGURE !!! overlap
-
-To understand the composition of the monomer layers, we ran simulations
-created using between 4 and 8 monomers in each layer. All configurations 
-were run for at least 200 ns. We showed that we can rule out systems 
-consisting of 4, 7, and 8 monomers based purely on comparison of 
-simulated pore spacing to experimental measurements.
-(Table~\ref{table:p2p}).
-
-The stability of crystalline phases is strongly dependent on temperature,
-requiring evaluation of our force field's ability to represent the 
-temperature at which we are simulating. All simulations were run and 
-equilibrated at 280K. To observe temperature dependent behavior, 
-the system temperature of 280K equilibrations were changed and the system
-was equilibrated again. Phase B is stable at all temperatures with 
-Phase A is stable at 280K. When temperature is raised to 300K, it is also
-stable, however there is a larger degree of disorder. We see a transition
-to Phase B in all cases when the temperature is raised above 310K 
-(~\ref{fig:transition}).
-
-        %MRS2: Tables should also have specific theses as well, so think about that.  Merely saying ``here is the information'' isn't as useful without a guide through it.
-	A summary of all experiments and relevant structural parameters are presented in Table ~\ref{table:p2p}
-
-\begin{figure}
-\centering
-\begin{subfigure}{0.3\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{placeholder.png}
-	\caption{}\label{fig:orderparameter}
-\end{subfigure}
-\begin{subfigure}{0.3\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{placeholder.png}
-	\caption{}\label{fig:order}
-\end{subfigure}
-\begin{subfigure}{0.3\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{placeholder.png}
-	\caption{}\label{fig:disorder}
-\end{subfigure}
-\caption{(a) As temperature is increased, Phase A transitions to Phase B, becoming more disordered.
-An order parameter of 1 indicates perfect ordering, while 0 indicates disorder.
-(b) The system is ordered, characteristic of Phase A, initially (c) The system becomes disordered, characteristic of Phase B, as temperature is raised beyond 310K}\label{fig:transition}
-%MRS2: maybe provide a bit more information what data will be here?  Order parametr vs time? One panel with order paramter vs. time, one with configurations from 0 and 1 endpoints?
-\end{figure}
-
-\begin{table}
-\centering
-\begin{tabular}{|c|c|}
-\hline
-table & here \\
-\hline
-\end{tabular}
-\caption{The pore spacing of the model increases as number of monomers in each layer increases.
-The pore spacing of a system starting in the sandwiched configuration is systematically lower than that started in an offset configuration.
-Systems built with 5 monomers per layer in a parallel displaced configuration results in a pore spacing closest to experimental data}\label{table:p2p}
-\end{table}
-
-\begin{figure}
-\centering
-\begin{subfigure}{.45\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{placeholder.png}
-	\caption{}\label{fig:phaseA}
-\end{subfigure}
-\begin{subfigure}{.45\textwidth}
-	\includegraphics[width=\linewidth]{placeholder.png}
-	\centering
-	\caption{}\label{fig:phaseB}
-\end{subfigure}
-\caption{There are clear differences in pore structure between systems built with layers stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
-%MRS2: explain theses?
-Also, the exact configurations used to start them are probably not that important; many different initial configurations will probably lead to most of them.
-It's the thermodyamics that are important.
-%BJC: okay, so just rephrase it, worded in a way that doesn't reference the initial configuration/layer spacing?
-%BJC: what do you  mean by 'thermodynamics that are important' -- just distinguishing which state is more favorable under what conditions?
-\label{fig:porestructures}
-\end{figure}
-%BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
-%MRS2: a little hard to say until the data is in.
-
-	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
-	\begin{itemize}
-		\item Phase A
-		\begin{itemize}	
-			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
-			\item There is evidence that the stacked configuration will shift towards an offset configuration over time.
-WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
-			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
-			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
-		\end{itemize}
-		\item Phase B
-		\begin{itemize}
-			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
-			\item No spots at all which is consistent with the disorder shown by the rings in the pore
-		\end{itemize}
-		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\textsuperscript{-1} which is typical of packed alkane chains
-		\item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B, 
-%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
-they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present   
-%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
-%BJC2: Are you thinking about the fourier transforms? I could bring that in
-	\end{itemize}
-
-	\begin{figure}
-	\centering
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:xrdA}}
-	\end{subfigure}
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:xrdexp}}
-	\end{subfigure}
-        \begin{subfigure}{.3\textwidth}
-                \centering
-                \includegraphics[width=\linewidth]{placeholder.png}
-                \caption{~\label{fig:xrdB}}
-        \end{subfigure}
-	\caption{Phase A (a) provides a good match to experiment (b).
-Phase B (c) is missing reflections present in the experimental pattern} % BJC: any more detail?
-%MRS2: yes, give distances, and describe what you mean as ``good match''
-%BJC2: what is a clear way to describe the spots in the ring. Diagonal reflections? radial spots?
-	\label{fig:xrd}
-	\end{figure}
-
-The model gives reasonable estimates of ionic conductivity for both phases.
-Calculated values of ionic conductivity obtained using the Nernst Einstein
-relation and Collective Diffusion model are compared in Table~\ref{table:conductivity}.
-The two methods agree with each other within error, although the 
-uncertainty obtained using the Collective Diffusion model is much higher.
-For this reason we will likely only use the Nernst Einstein relation
-in future calculations of this type. It is evident that the ordered 
-phase has a higher ionic conductivity than the disordered phase. 
-Conductivity is enhanced in Phase A because the pores are more open,
-increasing the likelihood of site hopping. In all cases, our calculated values
-are higher than experimental values, as expected. The real system, 
-although mostly aligned and straight, still has a distribution of 
-azimuthal angles, lowering the effective ionic conductivity of the bulk 
-membrane. The ordering from isotropic to mostly aligned mesophases 
-showed an 85 fold increase in ionic conductivity. We would expect additional
-gains in a perfect system.
-
-\begin{table}
-\centering
-\begin{tabular}{ccc}
-\toprule
-\multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
-\hline
-Method & Phase A & Phase B \\
-\midrule
-Nernst Einstein & \num{8e-5} & \num{8e-5} \\
-Collective Diffusion & \num{6e-5} & \num{6e-5} \\
-Experiment & \num{1.3e-5} & \num{1.3e-5} \\
-\bottomrule
-\end{tabular}
-\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error.
-Both methods give calculated values of ionic conductivity which are higher, but reasonably close to experimental values~\label{table:conductivity}}
-%MRS2: I would say that they are reasonable close to experiment, though higher. Also somewhat contradicted in other places.
-	\end{table}
-
-	The procedure used to create and validate our model can be used to evaluate other liquid crystalline assemblies.
-Using the design framework and analysis methods applied herin, we have the ability to reliably predict structures of new nanoporous membranes.
+The procedure used to create and validate our model can be used
+to evaluate other liquid crystalline assemblies. Using the design 
+framework and analysis methods applied herin, we have the ability 
+to reliably predict structures of new nanoporous membranes.

### 2017-08-15 Ben_Manuscripts/Masters_Bypass/conclusion.tex
additions

@@
-The procedure used to create and validate our model can be used
-to evaluate other liquid crystalline assemblies. Using the design 
-framework and analysis methods applied herin, we have the ability 
-to reliably predict structures of new nanoporous membranes.
+\section{Conclusion}
+
+In this work, we have illustrated a more detailed picture of the structure 
+of a self-assembled thermotropic liquid crystal membrane using an atomistic 
+molecular model. Using the model we have learned that these liquid crystal
+monomers prefer to stack in a sandwiched configuration with five monomers
+in each layer. By a thorough analysis of the membrane structure, we have
+discovered the existence of two metastable basins that both persist at room
+temperature. Structurally, Basin A matches closest to experiment, while 
+Basin B has not been seen experimentally. We hypothesize that Basin B will
+be dominant at higher temperatures. This hypothesis will be tested in future 
+work. In addition to structural accuracy, our model's physical properties
+are consistent with experimental measurements. Ionic conductivity, calculated
+in two ways, is in reasonable agreement with experiment. The procedure used
+to create and validate our model can be used to evaluate other liquid 
+crystalline assemblies. Using the design framework and analysis methods 
+applied herin, we have the ability to understand structures of new and
+unsynthesized nanoporous membranes.

### 2017-08-15 Ben_Manuscripts/Masters_Bypass/intro.tex
Update intro.tex

--- 2017-07-27 Ben_Manuscripts/Paper1/intro.tex
@@
 \cite{feng_scalable_2014}. In 2016, Feng et al. showed that the same 
-result could be obtained using a technique called soft confinement
+result could be obtained using a technique termed soft confinement
 \cite{feng_thin_2016}. Following this breakthrough, research into LLC
@@
 % side of the membrane.
-rejecting on the basis of shape and size, rather than just hydrodynamic
+on the basis of shape and size, rather than just hydrodynamic
 radius. An atomistic understanding of pore structure and its influence on
@@
 assembly in this system is thought to be pi-stacking interactions
-between aromatic headgroups\cite{gazit_possible_2002}. Gas phase ab
+between aromatic headgroups \cite{gazit_possible_2002}. Gas phase ab
 initio studies of benzene dimers have shown a clear energetic advantage
@@
 We must show that the developed molecular model is consistent with
-physical observations so that we can trust conclusions drawn about % better word for trust?
+physical observations so that we can rely on conclusions drawn about % better word for trust?
 structural features characteristic of the system. This article will
@@
 2D patterns. We calculate ionic conductivity using two agreeing methods.
-We examined the the influence of crosslinking on
-membrane structure. The analysis used in this paper can be readily
-extended to the H\textsubscript{II} phase and other similar LC systems.
+We examined the the influence of crosslinking on membrane structure. 
+The analysis used in this paper can be readily extended to the 
+H\textsubscript{II} phase and other similar LC systems.
 % Thesis: Our model needs to be consistent with experimental observations

### 2017-08-15 Ben_Manuscripts/Masters_Bypass/methods.tex
Formatting update

--- 2017-08-07 Ben_Manuscripts/Paper1/methods.tex
@@
-\section{Methods}
+\section*{Methods}
 
@@
 interactions between stacked aromatic rings\cite{feng_scalable_2014}. 
-Our simulations tend to equilibrate to a wider interlayer spacing of \approx 4.1 \angstrom,
+Our simulations tend to equilibrate to a wider interlayer spacing of $\approx$ 4.1 \angstrom,
 which inspired separate systems starting with layer spacings $>$ 4 \angstrom.

### 2017-08-15 Ben_Manuscripts/Masters_Bypass/results.tex
Formatting update

@@
-\section{Results and Discussion}
+\section*{Results and Discussion}
 
@@
 line is located at exactly half the qz value of R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
-real space periodic spacing of 7.4 \angstroms. This reflection has been 
+real space periodic spacing of 7.4 \angstrom. This reflection has been 
 attributed to 2\textsubscript{1} helical ordering of aromatic rings along the
@@
 a low intensity ring located at r = 1.4 \angstrom \textsuperscript{-1}. The
-real space separation corresponds to 4.5 \angstroms which is characteristic
+real space separation corresponds to 4.5 \angstrom which is characteristic
 of the average spacing between packed alkane chains. This reflection will be
 called R-alkanes. Within R-alkanes, are four spots of higher intensity which 
-will be called R-spots. All are located \approx 40 degrees from the qz axis
+will be called R-spots. All are located $\approx 40$ degrees from the qz axis
 in their respective quadrants. In many liquid crystal systems this can be
@@
 stacking modes. In each pattern, R-alkanes is present at a distance of
-$\approx$ 1.5 \angstrom \textsuperscript{-1}. R-pi is also present in each 
+$\approx 1.5$ \angstrom \textsuperscript{-1}. R-pi is also present in each 
 pattern, although it appears to intersect R-alkanes because the spacing
@@
 explained by our model's inability to appropriately represent aromatic interactions.
-The rings prefer to stack \approx 4.1 \angstrom apart as opposed to 3.7 \angstrom.
+The rings prefer to stack $\approx 4.1 \angstrom$ apart as opposed to 3.7 \angstrom.
 R-helix and R-spots are both missing. The line which intersected both of these

### 2017-08-16 Ben_Manuscripts/Masters_Bypass/methods.tex
edits

@@
 slow self-assembly process, python scripts are used to assemble 
-monomers into a structure close to the expected equilibrium configuration.
+monomers into a structure close to the expected equilibrium configuration (Fig~\ref{fig:python})
 A short, restrained equilibration, followed by NPT simulations $>$ 500 ns, 
@@
 % Unit Cell building method and justification
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{build.PNG}
+	\caption{(a) Single monomers are parameterized and annealed to produce a low energy
+		configuration. (b) Monomers are rotated and assembled into layers with 
+		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
+		a pore. (d) Pores are duplicated and place in a monoclinic unit cell}\label{fig:python}
+\end{figure}
 

### 2017-08-16 Ben_Manuscripts/Masters_Bypass/results.tex
edits

@@
 a 1D curve which has also been done.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.47\linewidth}
+		\centering
+		\includegraphics[width=\linewidth, valign=t]{WAXS_soft_confined.png}
+		\caption{}\label{fig:WAXS}
+	\end{subfigure}
+	\begin{subfigure}{0.43\linewidth}
+		\centering
+		\vspace{12mm}
+		\includegraphics[width=\linewidth]{SAXS.png}
+		\caption{}\label{figs:SAXS}
+	\end{subfigure}
+	\caption{(a) 2D wide angle X-ray scattering gives details about repeating features less than 1 nanometer apart (b) 1D small angle X-ray scattering indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
+\end{figure}
 

### 2017-08-16 Ben_Manuscripts/Outlines/Paper1_Outline.tex
Update Paper1_Outline.tex

@@
 
+Basin A and Basin B are two configurationally metastable basins. 
+\begin{itemize}
+	\item We hesitate to classify the basins as separate phases
+	\item We hypothesize that Basin B is present at higher temperatures
+	\item This is evidenced by a simulation of a system in Basin A whose temperature was linearly ramped from 280K to 340K over 100 ns
+	\item Visually, there is a distinct change in pore structure
+	\item To quantify our observations we chose 3 easily measurable order parameters: the distance between pores, the membrane the thickness and the ratio of pore radius to the uncertainty in pore radius.
+	\item The distance between pores was measured as described previously
+	\item The membrane thickness was measured using the length of the z-box vector
+	\item The pore radius was measured by calculating the distance between the center of mass of each aromatic ring and the center of mass of all aromatic rings in respective pores.
+	\item The pore radius is divided by its uncertainty in order to understand the degree to which monomers obstruct the pore region.
+	\item We observe changes in slope around 310K indicating the possibility of an abrupt change in system ordering
+	\item To prove that the basins are in fact two different phases, we search for a first order phase transition, which would be indicated by a discontinuity in an order parameter.
+	\item Our 100 ns temperature ramp may have been to fast to avoid hysteresis
+	\item To mitigate hysteresis, we started with structures equilibrated at 280K. The temperature was raised to 300K and allowed to equilibrate for 200 ns.
+	\item At the end of 200 ns, the temperature was raised 5K and equilibrated again for 200 ns. This processed continued until we reached 325K. 
+	\item We observed only smooth changes in order parameters as temperature was increased indicating that we have not found two phases.
+\end{itemize}
+
 	We varied the relative interlayer orientation between sandwiched and parallel-displaced based on our knowledge of the stability of these two pi-stacking modes.

### 2017-08-16 Ben_Manuscripts/Masters_Bypass/results.tex
Update results.tex

@@
 % There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
+
+Basin A and Basin B are two configurationally metastable basins. 
+\begin{itemize}
+	\item We hesitate to classify the basins as separate phases
+	\item We hypothesize that Basin B is present at higher temperatures
+	\item This is evidenced by a simulation of a system in Basin A whose temperature was linearly ramped from 280K to 340K over 100 ns
+	\item Visually, there is a distinct change in pore structure
+	\item To quantify our observations we chose 3 easily measurable order parameters: the distance between pores, the membrane the thickness and the ratio of pore radius to the uncertainty in pore radius.
+	\item The distance between pores was measured as described previously
+	\item The membrane thickness was measured using the length of the z-box vector
+	\item The pore radius was measured by calculating the distance between the center of mass of each aromatic ring and the center of mass of all aromatic rings in respective pores.
+	\item The pore radius is divided by its uncertainty in order to understand the degree to which monomers obstruct the pore region.
+	\item We observe changes in slope around 310K indicating the possibility of an abrupt change in system ordering
+	\item To prove that the basins are in fact two different phases, we search for a first order phase transition, which would be indicated by a discontinuity in an order parameter.
+	\item Our 100 ns temperature ramp may have been to fast to avoid hysteresis
+	\item To mitigate hysteresis, we started with structures equilibrated at 280K. The temperature was raised to 300K and allowed to equilibrate for 200 ns.
+	\item At the end of 200 ns, the temperature was raised 5K and equilibrated again for 200 ns. This processed continued until we reached 325K. 
+	\item We observed only smooth changes in order parameters as temperature was increased indicating that we have not found two phases.
+\end{itemize}
 

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/intro.tex
revisions

@@
 separations of small molecules can be achieved using reverse osmosis 
-(RO) or nanofiltration (NF)\cite{van_der_bruggen_review_2003}.
+(RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}.
 
@@
 RO membranes are unstructured with tortuous and polydisperse diffusion
-pathways which leads to inconsistent performance\cite{song_nano_2011}.
+pathways which leads to inconsistent performance \cite{song_nano_2011}.
 Necessarily high feed pressures drive up energy requirements which 
 strain developing regions and contribute strongly to CO\textsubscript{2} 
-emissions\cite{mcginnis_global_2008}. Moreover, designing RO 
+emissions \cite{mcginnis_global_2008}. Moreover, designing RO 
 membranes to achieve targeted separations of specific solutes is nearly
 impossible because various solutes dissolve into and diffuse through the polymer
-matrix at different rates\cite{wijmans_solution-diffusion_1995}. At best,
+matrix at different rates \cite{wijmans_solution-diffusion_1995}. At best,
 one can exploit these differences to create a functional selective 
@@
 drive down energy requirements while still affording separation of 
-solutes as small as ions to some degree\cite{van_der_bruggen_review_2003}.
+solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}.
 This is why NF is often used as a precursor to reverse osmosis. 
@@
 separations by tuning size and functionality of the molecular building
-blocks which form these materials. Solute rejecting pore sizes can be  % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
-tuned uniformly, resulting in sharp size cut-offs. Entirely different
-mechanisms may govern the separation processes in a given nanostructured
-material which can inspire novel separation techniques.
+blocks which form these materials. Solute rejecting pores can have their  % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
+size tuned uniformly, resulting in sharp size cut-offs. Entirely different
+mechanisms may govern transport in a given nanostructured material which
+can inspire novel separation techniques.
 % Thesis: Nanostructured materials can overcome issues seen in RO and NF
@@
 monodispersity \cite{hata_water-assisted_2004,maruyama_growth_2005}.
-Zeolites have sub-nm pores with a narrow size distribution and MD simulations
+Zeolites have sub-nm pores with a narrow pore size distribution and MD simulations
 exhibit complete rejection of solvated ions \cite{murad_molecular_1998},
@@
 structures with the added benefits of low cost and synthetic techniques
-feasible for large scale production\cite{feng_scalable_2014}. LLCs are
+feasible for large scale production \cite{feng_scalable_2014}. LLCs are
 versatile and controllable with a large chemical design space available
 for membrane design. We will be studying assemblies formed by Na-GA3C11 
-(Figures~\ref{fig:chemdraw} and ~\ref{fig:monatomistic}), a system which
-has been extensively studied experimentally\cite{smith_ordered_1997,
+(Fig~\ref{fig:python}a), a system which
+has been extensively studied experimentally \cite{smith_ordered_1997,
 zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
@@
 \cite{feng_thin_2016}. Following this breakthrough, research into LLC
-membranes has been reinvigorated. We have chosen to focus our efforts 
+membranes has been reinvigorated. We have chosen to focus our initial efforts 
 on the development of a model of the Col\textsubscript{h} phase membrane
@@
 
-\begin{figure}
-\centering
-\begin{subfigure}{.45\linewidth}
-	\centering
-        \includegraphics[width=\linewidth]{placeholder.png}
-        \caption{}\label{fig:chemdraw}
-\end{subfigure}
-\begin{subfigure}{.45\linewidth}
-	\centering
-        \includegraphics[width=\linewidth]{placeholder.png}
-        \caption{}\label{fig:monatomistic}
-\end{subfigure}
-\medskip
-\begin{subfigure}{.45\linewidth}
-	\centering
-        \includegraphics[width=\linewidth]{placeholder.png}
-        \caption{}\label{fig:cartoonlayer}
-\end{subfigure}
-\begin{subfigure}{.45\linewidth}
-	\centering
-        \includegraphics[width=\linewidth]{placeholder.png}
-        \caption{}\label{fig:layeratomistic}
-\end{subfigure}
-\caption{(a) The chemical structure of NAGA3C11 (b) The chemical 
-structure visualized atomistically enhances intuition about system
-behavior (c) Wedge-shaped monomers assemble into layers (d) An atomistic
-view of a layer suggests geometric constraints based on monomer
-structure}\label{fig:cartoonvatomistic}
-\end{figure}
-%BJC: maybe add 2 more panels with full assemblies represented with
-% a cartoon and atomistically
-
 A molecular level understanding of LLC membrane structure will elucidate
@@
 membranes. We do not yet understand how to reduce the effective pore
-size or how to tune the chemical environment in the H\textsubscript{II} 
+size or how to tune the chemical environment in the 
 nanopores for effective water desalination and small organic separations.
-Rejection studies show that this membrane can not perform desalination yet 
-because the pores are too large\cite{zhou_supported_2005}. Over the past
+Rejection studies show that this membrane can not perform separations of solutes less than 1.2 nm  
+because the pores are too large \cite{zhou_supported_2005}. Over the past
 20 years, LLC membrane studies have been limited primarily 
 to Na-GA3C11 with some characterization done after minor structural 
-modifications\cite{resel_structural_2000}. Optimization has been 
+modifications \cite{resel_structural_2000}. Optimization has been 
 performed through trial and error. The only source of predictive modeling  % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
@@
 questions.
-The arrangement of sodium ions
+The arrangement of monomers
 in the channels is thought to be confined to the pore walls. It is 
@@
 Col\textsubscript{h} phase is described as having pores made of disks or
-layers (Figure~\ref{fig:cartoonlayer},~\ref{fig:layeratomistic}) stacked
+layers stacked
 on top of one another, each containing a set number of monomers. A 
@@
 One of the driving forces for self % reference something with self assembly of aromatic compounds
-assembly in this system is thought to be pi-stacking interactions
+assembly in this system is thought to be pi-pi stacking interactions
 between aromatic headgroups \cite{gazit_possible_2002}. Gas phase ab
 initio studies of benzene dimers have shown a clear energetic advantage
-for parallel displaced and T-shaped pi-stacking conformations versus a
+for parallel displaced and T-shaped pi-pi stacking conformations versus a
 sandwiched conformation~\cite{sinnokrot_estimates_2002}.
-Substituted benzene rings exhibit an even stronger pi-stacking 
+Substituted benzene rings exhibit an even stronger pi-pi stacking 
 attraction which favors the parallel displaced configuration in all cases

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/methods.tex
revisions

@@
 HII monomers were parameterized using the Generalized AMBER Forcefield
-\cite{wang_development_2004} with the Antechamber package\cite{wang_automatic_2006}
-provided with AmberTools16\cite{case_ambertools16_2016}. Charges were
+\cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
+provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
 assigned using tools from Openeye Scientific Software. All molecular 
-dynamics simulations were run using Gromacs version 5.1.2 and Gromacs 
-version 2016. \cite{bekker_gromacs:_1993,berendse n_gromacs:_1995,
+dynamics simulations were run using the latest version of Gromacs 2016. \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,
 van_der_spoel_gromacs:_2005,hess_gromacs_2008}
@@
 configurations were pulled from the trajectory to be used for full
-system construction.
+system construction (Figure~\ref{fig:python}a).
 % monomer parametrization
@@
 simulation, calling for a more efficient way to build the system. 
-Previous work has shown a coarse grain model self assemble into the HII
+Previous work has shown a coarse grain model self assemble into the H\textsubscript{II}
 phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
 Atomistic self-assembly was attempted by packing monomers into a box 
-using Packmol\cite{martinez_packmol:_2009}. Simulations of $>$ 100 ns 
+using Packmol \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns 
 show no indicators of progress towards an ordered system. To bypass the
 slow self-assembly process, python scripts are used to assemble 
-monomers into a structure close to the expected equilibrium configuration (Fig~\ref{fig:python})
-A short, restrained equilibration, followed by NPT simulations $>$ 500 ns, 
+monomers into a structure close to the expected equilibrium configuration (Figure~\ref{fig:python}).
+A short, restrained equilibration, followed by NPT simulations between 400 and 500 ns, 
 allows the initial configuration to relax into an equilibrium configuration.
@@
 to allow us to look at longer timescales. Ultimately, we chose to build a system
-with 20 monomer layers each pore in order to give sufficient
+with 20 monomer layers in each pore in order to give sufficient
 resolution when simulating X-ray diffraction patterns.  % BJC: reword / mention xrd resolution - system size dependence in previous sentence
@@
 data for this system \cite{feng_thin_2016}. Initial configuration pore
-spacing was chosen to be 10 \% larger than the experimental value. 
+spacing was chosen to be 10 \% larger than the experimental value to reduce
+unintended repulsions resulting from a tightly packed initial configuration. 
 The layer spacing was based on experimental 2D WAXS data which shows
@@
 been hypothesized that the features are present due to pi-pi
-interactions between stacked aromatic rings\cite{feng_scalable_2014}. 
+interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
 Our simulations tend to equilibrate to a wider interlayer spacing of $\approx$ 4.1 \angstrom,
-which inspired separate systems starting with layer spacings $>$ 4 \angstrom.
-Initial pore radius estimates were based on past TEM 
+which inspired separate systems starting with layer spacings greater than
+ 4 \angstrom. Initial pore radius estimates of 0.6 nm were based on past TEM 
 images and size exclusion rejection data\cite{feng_scalable_2014,
@@
 data as well as the various known stacking modes of benzene and substituted 
-benzene rings: sandwiched, T-shaped and parallel-displaced. The T-shaped configuration was ruled
-% BJC: Figure showing benzene pi-stacking modes and 
-out based on the inconsistency of its $\approx$ 5 \angstrom equilibrium 
-stacking distance with diffraction data. The system's preference
+benzene rings: sandwiched, parallel-displaced and T-shaped 
+(Figures~\ref{fig:sandwiched,fig:pd,fig:tshaped}). The T-shaped 
+configuration was ruled out based on the inconsistency of its $\approx$ 
+5 \angstrom equilibrium stacking distance. The system's preference
 towards the sandwiched vs. parallel displaced stacking modes was left
-to be explored. Visualization of each configuration suggests entropic differences 
-based on the way the tails are able to pack. This difference may 
-explain, in part, which stacking mode is more favorable.
+to be explored. Visualization of each configuration 
+(Figures~\ref{fig:sandwiched_layers,fig:offset_layers} suggests 
+entropic differences based on the way the tails are able to pack. 
+This difference may explain, in part, which stacking mode is more favorable.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{sandwiched.png}
+		\caption{}\label{fig:sandwiched}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{PD.png}
+		\caption{}\label{fig:pd}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Tshaped.png}
+		\caption{}\label{fig:tshaped}
+	\end{subfigure}
+	\vskip\baselineskip
+	\begin{subfigure}[b]{0.475\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{sandwiched_layers.png}
+		\caption{}\label{fig:sandwiched_layers}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.475\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{offset_layers.png}
+		\caption{}\label{fig:offset_layers}
+	\end{subfigure}
+	\caption{}\label{fig:stacking}
+\end{figure}
 
@@
 potential. The resulting unrestrained structure is allowed to 
-equilibrate in the NPT ensemble for $>$ 200 ns.  % should probably run all of them to x ns rather than making it ambiguous
+equilibrate in the NPT ensemble for 400 - 500 ns.
 
@@
 boundaries. The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
-constant under a range of simulation conditions (see supplemental info). 
-% BJC: This paragraph could be shortened and some of it put in the supplemental info, but I like it here for now
+constant under a range of simulation conditions.
 
@@
 dimensional fourier transform (FT) of the array of electron density 
-results in a 3 dimensional representation of the unit cell in reciprocal
-space. Cross sections of the 3D FT result in two dimensional reciprocal
-space patterns which represent 2D diffraction patterns. Spherical
-integration of the FT yields a 1 dimensional curve which is the same
-as that generated in a diffraction experiment. We matched experimental
-1D and 2D WAXS patterns by iterative improvement of our choice of 
-initial structure and equilibration procedure 
-% Replace with a description written by Joe
+results in a 3 dimensional structure factor representing the unit cell
+in reciprocal space. We perform an angular average of the structure factor
+about the z axis to generate a 2D cross section close to what one would see
+experimentally. We matched experimental 2D WAXS patterns by iterative
+improvement of our choice of initial structure and equilibration procedure. 
+% Replace with a description written by Joe eventually
 
@@
 coefficients were found by calculating the slope of the linear
-region of the mean square displacement curve as indicated by the einstein relation
-\cite{einstein_investigations_1956}. Ion concentration was measured with
-respect to the entire unit cell. The second method, termed the 'Collective
-Diffusion' model \cite{liu_collective_2013}, measures the movement of
-the collective variable, Q, which is defined as the amount of charge 
-transfer through the system. The diffusion coefficient of Q, $D_Q$, can
-be calculated using the einstein relation. The conductance, $\gamma$ of
-the system can be calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$ 
-Conversion to ionic conductivity is achieved by multiplying by channel 
-length and dividing by the membrane cross sectional area. A full 
-derivation of the model can be accessed elsewhere\cite{liu_collective_2013}.  
+region of the mean square displacement curve as indicated by the
+einstein relation \cite{einstein_investigations_1956}. Ion concentration
+was measured with respect to the entire unit cell. The second method, 
+termed the 'Collective Diffusion' model \cite{liu_collective_2013}, 
+measures the movement of the collective variable, Q, which is defined as
+the amount of charge transfer through the system. The diffusion 
+coefficient of Q, $D_Q$, can be calculated using the einstein relation.
+The conductance, $\gamma$ of the system can be calculated as:
+$$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
+achieved by multiplying by channel length and dividing by the membrane
+cross sectional area. A full derivation of the model can be accessed 
+elsewhere \cite{liu_collective_2013}.  
 % Talk about error somewhere?

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/methods.tex
updates

@@
 benzene rings: sandwiched, parallel-displaced and T-shaped 
-(Figures~\ref{fig:sandwiched,fig:pd,fig:tshaped}). The T-shaped 
+(\Cref{fig:sandwiched,fig:pd,fig:tshaped}). The T-shaped 
 configuration was ruled out based on the inconsistency of its $\approx$ 
@@
 to be explored. Visualization of each configuration 
-(Figures~\ref{fig:sandwiched_layers,fig:offset_layers} suggests 
+(\Cref{fig:sandwichedlayers,fig:offsetlayers}) suggests 
 entropic differences based on the way the tails are able to pack. 
@@
 		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{}\label{fig:sandwiched}
+		\caption{Sandwiched}\label{fig:sandwiched}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{PD.png}
-		\caption{}\label{fig:pd}
+		\caption{Parallel-Displaced}\label{fig:pd}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{}\label{fig:tshaped}
+		\caption{T-shaped}\label{fig:tshaped}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\textwidth]{sandwiched_layers.png}
-		\caption{}\label{fig:sandwiched_layers}
+		\includegraphics[width=\textwidth]{sandwichedlayers.png}
+		\caption{Two monomer layers stacked in the sandwiched configuration}\label{fig:sandwichedlayers}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\textwidth]{offset_layers.png}
-		\caption{}\label{fig:offset_layers}
+		\includegraphics[width=\textwidth]{offsetlayers.png}
+		\caption{Two monomer layers stacked in the parallel-displaced configuration}\label{fig:offsetlayers}
 	\end{subfigure}

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
revisions
updates

--- 2017-08-16 Ben_Manuscripts/Masters_Bypass/results.tex
@@
 
-To understand the composition of the monomer layers, we ran simulations of 
+To discern the composition of the monomer layers, we ran simulations of 
 systems created with 4 - 8 monomers per layer. Both the sandwiched and 
@@
 respective pores. Statistics were generated using the bootstrapping 
-technique. Systems built with 5 monomers in each layer equilibrate to a pore
+technique. Table~\ref{table:p2p} shows the pore spacing for all systems tested.
+Systems built with 5 monomers in each layer equilibrate to a pore
 spacing that is most consistent with the experimental value of 4.12 nm
-derived from SAXS measurements (Table~\ref{table:p2p}). The remainder of
+derived from SAXS measurements (Figure~\ref{fig:SAXS}). The remainder of
 this discussion will focus on the analysis of systems built with 5 
@@
 The experimental 2D WAXS measurement contains five major reflections which
-our model intends to reproduce (Fig ~\ref{fig:WAXSexp}). The first is located
+our model intends to reproduce (Figure~\ref{fig:WAXS}). The first is located
 at qz = 1.7 \angstrom \textsuperscript{-1}, corresponding to a real space 
@@
 real space periodic spacing of 7.4 \angstrom. This reflection has been 
-attributed to 2\textsubscript{1} helical ordering of aromatic rings along the
+interpreted  as 2\textsubscript{1} helical ordering of aromatic rings along the
 z axis and will therefore be referred to as R-helix. If positions of the 
@@
 in their respective quadrants. In many liquid crystal systems this can be
-attributed to the tilt angle of the alkane chains with respect to the xy axis. 
+explained by the tilt angle of the alkane chains with respect to the xy plane. 
 The final major reflections correspond to the spacing and symmetry of the d100 
@@
 is easiest to interpret the data by radially integrating the 2D data to get 
-a 1D curve which has also been done.
+a 1D curve which is shown in Figure~\ref{fig:SAXS}.
 
@@
 	\centering
-	\begin{subfigure}{0.47\linewidth}
+	\begin{subfigure}[t]{0.47\linewidth}
 		\centering
-		\includegraphics[width=\linewidth, valign=t]{WAXS_soft_confined.png}
+		\raisebox{.2\textwidth}{%
+		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
+		}
 		\caption{}\label{fig:WAXS}
 	\end{subfigure}
-	\begin{subfigure}{0.43\linewidth}
+	\begin{subfigure}[t]{0.43\linewidth}
 		\centering
-		\vspace{12mm}
+	%	\vspace{12mm}
 		\includegraphics[width=\linewidth]{SAXS.png}
-		\caption{}\label{figs:SAXS}
+		\caption{}\label{fig:SAXS}
 	\end{subfigure}
@@
 open pore structure. Aromatic rings are arranged in a helical conformation.
-We will refer to this system as Basin A (Fig ~\ref{fig:phaseA}). Simulations
-of systems built with layers stacked > 4 \angstrom apart results in a pore
+We will refer to this system as Basin A (Figure~\ref{fig:280K_pore}). Simulations
+of systems built with layers stacked greater than 4 \angstrom apart results in a pore
 structure characterized by high radial disorder, while still maintaining 
 partitioning between hydrophobic and hydrophilic regions. This will be 
-called Basin B (Fig~\ref{fig:phaseB}). It is apparent that this LLC membrane
+called Basin B (Figure~\ref{fig:340K_pore}). It is apparent that this LLC membrane
 may exist in at least two metastable states. The distinct difference in 
-pore structure (Fig~\ref{fig:porestructures}) exhibited by each phase will
-likely lead to different transport mechanisms. Understanding which phase 
-exists experimentally is necessary in order to appropriately study the system.
+pore structure exhibited by each phase will likely lead to different transport
+mechanisms. Understanding which phase exists experimentally is necessary in 
+order to appropriately study the system.
 % BJC: include more examples of the difference between the two basins
@@
 % There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
+
+Basin A and Basin B are two configurationally metastable basins. 
+We hesitate to classify the basins as separate phases. We hypothesize
+that Basin B is present at higher temperatures. This is evidenced by
+a simulation of a system in Basin A whose temperature was linearly
+ramped from 280K to 340K over 100 ns. Visually, there is a distinct
+change in pore structure from one characteristic of Basin A 
+(Figure~\ref{fig:280K_pore} to one characteristic of Basin B 
+(Figure~\ref{fig:340K_pore}. To quantify our observation, we chose 
+three easily measurable order parameters: the distance between pores,
+the membrane the thickness and the ratio of pore radius to the uncertainty
+in pore radius. The distance between pores was measured as described 
+previously. The membrane thickness was measured using the length of the
+z box vector. The pore radius was measured by calculating the distance
+between the center of mass of each aromatic ring and the center of mass
+of all aromatic rings in respective pores. The pore radius is divided by
+its uncertainty in order to understand the degree to which monomers 
+obstruct the pore region. Referring back to our temperature ramped system,
+the slope of all order parameters change around 310K indicating the 
+possibility of an abrupt change in system ordering. To prove that the 
+basins are in fact two different phases, we must observe evidence of a
+first order phase transition, which would be indicated by a discontinuity
+in an order parameter as a function of temperature. Our 100 ns temperature
+ramp may have been too fast and may have suffered hysteresis. To mitigate
+hysteresis, we performed a slow, stepwise temperature ranp. Started from
+structures equilibrated at 280K, the system temperature was raised to 
+300K and allowed to equilibrate for 200 ns. At the end of 200 ns, the
+temperature was raised 5K and equilibrated again for 200 ns. We repeated
+this process until the system was equilibrated for 200 ns at 325K. In all
+cases, we observed smooth changes in order parameters as temperature was
+increased implying that we have not found two phases.
+
+\begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+                \caption{}\label{fig:280K_pore}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{340K_tramp_close.png}
+                \caption{}\label{fig:340K_pore}
+        \end{subfigure}
+        \vskip\baselineskip
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{p2p_tramp.png}
+                \caption{}\label{fig:p2p_tramp}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{thickness_tramp.png}
+
+                \caption{}\label{fig:thickness_tramp}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{order_tramp.png}
+                \caption{}\label{fig:order_tramp}
+        \end{subfigure}
+        \caption{}\label{fig:tramp}
+\end{figure}
 
@@
 in aromatic ring spacing between experiment and simulation is likely a result
-of the inability of GAFF to properly handle pi interactions. The parallel
+of the inability of GAFF to properly handle aromatic interactions. The parallel
 displaced configuration contains two lines of high intensity with maximum
@@
 contains all features except for R-helix. Most notably, R-spots appears in the
-expected location, which suggests that there is something intrinsically to
+expected location, which suggests that there is something intrinsic to
 the sandwiched packing which gives rise to such features. Finally, the 
-disordered structure exhibits R-alkanes and R-pores. R-helix are R-spots are not
+disordered structure exhibits R-alkanes and R-pores. R-helix and R-spots are not
 present. Given the evidence, the sandwiched configuration with layers spaced
@@
 nearly hexagonal array of packed tails.
+
+\begin{wrapfigure}{R}{0.4\textwidth}
+	\centering
+	\includegraphics[width=0.4\textwidth]{tilt.png}
+	\caption{The average angle between alkyl chains and the xy plane is nearly zero degrees}\label{fig:tilt}
+\end{wrapfigure}
 

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
Out with the old, in with the new figures

@@
 parallel displaced configurations were tested. All systems remained
-stable for at least 50 ns. Pair correlation functions calculated between 
-aromatic rings along the length of the pores indicate that systems prefer to
-stay partitioned into layers (Fig~\ref{fig:zdf}). Pore spacings were 
-calculated by measuring the distance between the pore centers. Pore centers
-were located by averaging the coordinates of sodium ions in their 
-respective pores. Statistics were generated using the bootstrapping 
-technique. Table~\ref{table:p2p} shows the pore spacing for all systems tested.
+stable for at least 50 ns. Pore spacings were calculated by measuring
+the distance between the pore centers. Pore centers were located by
+averaging the coordinates of sodium ions in their respective pores. 
+Statistics were generated using the bootstrapping technique. Table
+~\ref{table:p2p} shows the pore spacing for all systems tested.
 Systems built with 5 monomers in each layer equilibrate to a pore
@@
 this discussion will focus on the analysis of systems built with 5 
-monomers per layer.
+monomers per layer. Pair correlation functions calculated between 
+aromatic rings along the length of the pores indicate that systems
+prefer to stay partitioned into layers (Fig~\ref{fig:zdf}).
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|}
+\toprule
+                   & \multicolumn{2}{c}{Starting Configuration} \\
+Monomers per layer & Sandwiched & Parallel Displaced \\
+\midrule
+4 & $3.71 \pm 0.08$ & $3.82 \pm 0.06$ \\
+5 & $3.99 \pm 0.08$ & $4.16 \pm 0.09$ \\
+6 & $4.83 \pm 0.08$ & $4.85 \pm 0.05$ \\
+7 & $4.73 \pm 0.06$ & $4.84 \pm 0.06$ \\
+8 & $5.08 \pm 0.08$ & $5.46 \pm 0.07$ \\
+\bottomrule
+\end{tabular}
+\caption{The pore spacing of the model increases as number of monomers
+in each layer increases. The pore spacing of a system starting in the 
+sandwiched configuration is systematically lower than that started in an 
+offset configuration. Systems built with 5 monomers per layer in a parallel
+displaced configuration results in a pore spacing closest to experimental
+data}\label{table:p2p} 
+\end{table}
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{zdf5layered.png}
+		\caption{}\label{fig:zdf_layered}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{zdf5offset.png}
+		\caption{}\label{fig:zdf_offset}
+	\end{subfigure}
+\end{figure}
 
@@
 change in pore structure from one characteristic of Basin A 
-(Figure~\ref{fig:280K_pore} to one characteristic of Basin B 
-(Figure~\ref{fig:340K_pore}. To quantify our observation, we chose 
+(Figure~\ref{fig:280K_pore}) to one characteristic of Basin B 
+(Figure~\ref{fig:340K_pore}). To quantify our observation, we chose 
 three easily measurable order parameters: the distance between pores,
@@
 obstruct the pore region. Referring back to our temperature ramped system,
-the slope of all order parameters change around 310K indicating the 
+the slope of all order parameters change around 310K 
+(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
 possibility of an abrupt change in system ordering. To prove that the 
@@
 in an order parameter as a function of temperature. Our 100 ns temperature
-ramp may have been too fast and may have suffered hysteresis. To mitigate
-hysteresis, we performed a slow, stepwise temperature ranp. Started from
+ramp may have been too fast causing the system to suffer from hysteresis. To mitigate
+hysteresis, we performed a slow, stepwise temperature ramp. Starting from
 structures equilibrated at 280K, the system temperature was raised to 
@@
 temperature was raised 5K and equilibrated again for 200 ns. We repeated
-this process until the system was equilibrated for 200 ns at 325K. In all
+this process until the system was equilibrated for 200 ns at 320K. In all
 cases, we observed smooth changes in order parameters as temperature was
-increased implying that we have not found two phases.
+increased implying that we have not found two phases 
+(Figure~\ref{fig:phase_transition}).
 
@@
         \caption{}\label{fig:tramp}
+\end{figure}
+
+\beging{figure}
+	\centering
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{p2p_layered.png}
+		\caption{}\label{fig:p2p_layered}
+	\end{subfigure}
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{thickness_layered.png}
+		\caption{}\label{fig:thickness_layered}
+	\end{subfigure}
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{order_layered.png}
+		\caption{}\label{fig:order_layered}
+	\end{subfigure}
 \end{figure}
@@
 
-        %MRS2: Tables should also have specific theses as well, so think about that.  Merely saying ``here is the information'' isn't as useful without a guide through it.
-A summary of all experiments and relevant structural parameters are presented in Table ~\ref{table:p2p}
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:orderparameter}
-	\end{subfigure}
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:order}
-	\end{subfigure}
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{}\label{fig:disorder}
-	\end{subfigure}
-	\caption{(a) As temperature is increased, Phase A transitions to 
-	Basin B, becoming more disordered.
-An order parameter of 1 indicates perfect ordering, while 0 indicates disorder.
-(b) The system is ordered, characteristic of Phase A, initially (c) The system becomes disordered, characteristic of Phase B, as temperature is raised beyond 310K}\label{fig:transition}
-	%MRS2: maybe provide a bit more information what data will be here?  Order parametr vs time? One panel with order paramter vs. time, one with configurations from 0 and 1 endpoints?
-\end{figure}
-
-\begin{table}
-\centering
-\begin{tabular}{|c|c|}
-\hline
-table & here \\
-\hline
-\end{tabular}
-\caption{The pore spacing of the model increases as number of monomers in each layer increases.
-The pore spacing of a system starting in the sandwiched configuration is systematically lower than that started in an offset configuration.
-Systems built with 5 monomers per layer in a parallel displaced configuration results in a pore spacing closest to experimental data}\label{table:p2p}
-\end{table}
-
-\begin{figure}
-\centering
-\begin{subfigure}{.45\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{placeholder.png}
-	\caption{}\label{fig:phaseA}
-\end{subfigure}
-\begin{subfigure}{.45\textwidth}
-	\includegraphics[width=\linewidth]{placeholder.png}
-	\centering
-	\caption{}\label{fig:phaseB}
-\end{subfigure}
-\caption{There are clear differences in pore structure between systems built with layers stacked (a) 3.7 \angstrom apart and (b) 5.0 \angstrom apart}
-%MRS2: explain theses?
-Also, the exact configurations used to start them are probably not that important; many different initial configurations will probably lead to most of them.
-It's the thermodyamics that are important.
-%BJC: okay, so just rephrase it, worded in a way that doesn't reference the initial configuration/layer spacing?
-%BJC: what do you  mean by 'thermodynamics that are important' -- just distinguishing which state is more favorable under what conditions?
-\label{fig:porestructures}
-\end{figure}
-%BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
-%MRS2: a little hard to say until the data is in.
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:xrdA}}
-	\end{subfigure}
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{placeholder.png}
-		\caption{~\label{fig:xrdexp}}
-	\end{subfigure}
-        \begin{subfigure}{.3\textwidth}
-                \centering
-                \includegraphics[width=\linewidth]{placeholder.png}
-                \caption{~\label{fig:xrdB}}
-        \end{subfigure}
-	\caption{Phase A (a) provides a good match to experiment (b).
-Phase B (c) is missing reflections present in the experimental pattern} % BJC: any more detail?
-%MRS2: yes, give distances, and describe what you mean as ``good match''
-%BJC2: what is a clear way to describe the spots in the ring. Diagonal reflections? radial spots?
-	\label{fig:xrd}
-\end{figure}
-
 The model gives reasonable estimates of ionic conductivity for both phases.

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
restrained XRD figures
More Figures

@@
 
-\beging{figure}
+\begin{figure}
 	\centering
@@
 generated from each configuration establish a difference between the two
-stacking modes. In each pattern, R-alkanes is present at a distance of
+stacking modes (Figure~\ref{fig:XRDrestrained}). In each pattern, R-alkanes is present at a distance of
 $\approx 1.5$ \angstrom \textsuperscript{-1}. R-pi is also present in each 
@@
 
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.475\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{rzlayeredrestrained.png}
+		\caption{}\label{fig:rzplayeredrestrained}
+	\end{subfigure}
+	\begin{subfigure}{0.475\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{rzoffsetrestrained.png}
+		\caption{}\label{fig:rzoffsetrestrained}
+	\end{subfigure}
+	\caption{}\label{fig:XRDrestrained}
+\end{figure}
+
 Full comparison of experimental 2D WAXS with simulated X-ray diffraction
@@
 greater than 400 ns. Simulated diffration patterns were generated using 
-portions of the trajectory after equilibration. Equilibration was detected
+portions of the trajectory after equilibration (Figure~\ref{fig:XRDsim}). Equilibration was detected
 when the distance between pores and the membrane thickness stopped changing.
@@
 3.7 \angstrom apart gives rise to an equilibrated structure closest to experiment.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
+		\caption{}\label{fig:sandwich_rzplot}
+	\end{subfigure}
+	\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{offset_rzplot.png}
+		\caption{}\label{fig:offsetrzplot}
+	\end{subfigure}
+	\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{disorder_rzplot.png}
+		\caption{}\label{fig:disorder_rzplot.png}
+	\end{subfigure}
+	\caption{}\label{fig:XRDsim}
+\end{figure}
 
@@
 \end{wrapfigure}
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{tails_topview.png}
+		\caption{}\label{fig:tails_topview}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{tails_rzplot.png}
+		\caption{}\label{fig:tails_rzplot}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{centroids_box.png}
+		\caption{}\label{fig:centroids}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{angles_traj_layered.png}
+		\caption{}\label{fig:angle_distribution}
+	\end{subfigure}
+	\caption{}\label{fig:tail_packing}
+\end{figure}
 

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
adding captions

@@
 	\end{subfigure}
+	\caption{Pair distribution functions of aromatic carbons for the
+	(a) 5 monomer per layer, sanwiched and (b) 5 monomer per layer, 
+	parallel displaced configurations. Spikes in the distribution mark
+	distinct layers. The magnitude of the spikes with respect to the 
+	average suggest that the 5 monomer per layer, sandwiched configuration
+	possesses the highest degree of layer partitioning.}\label{fig:zdf}
 \end{figure}
@@
 	\end{subfigure}
-	\caption{(a) 2D wide angle X-ray scattering gives details about repeating features less than 1 nanometer apart (b) 1D small angle X-ray scattering indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
+	\caption{(a) 2D wide angle X-ray scattering gives details about repeating features less than 1 nanometer apart.
+(b) 1D small angle X-ray scattering indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
 \end{figure}
@@
 obstruct the pore region. Referring back to our temperature ramped system,
-the slope of all order parameters change around 310K 
+the slope of all order parameters change around 315K - 325K 
 (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
@@
 cases, we observed smooth changes in order parameters as temperature was
-increased implying that we have not found two phases 
-(Figure~\ref{fig:phase_transition}).
+increased implying that we can not yet claim the existence of two phases (Figure~\ref{fig:phase_transition}).
+The same process will continue to be repeated up to 340K in the near future
+since we have not surpassed the temperatures where we observe abrupt slope 
+changes in pore spacing and membrane thickness (\Cref{fig:p2p_tramp,fig:thickness_tramp}).
 
@@
         \end{subfigure}
-        \caption{}\label{fig:tramp}
+        \caption{(a) The open pore structure exhibited by a structure equilibrated
+	at 280K is characteristic of Basin A. (b) The closed pore structure with 
+	a high degree of radial disorder exhibited when the structure in (a) is 
+	heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
+	vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs. 
+	temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
+	its uncertainty changes slope near 315K.}\label{fig:tramp}
 \end{figure}
@@
 	\end{subfigure}
+	\caption{(a) }\label{fig:phase_transition}
 \end{figure}

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
more captions

@@
 	\end{subfigure}
-	\caption{(a) }\label{fig:phase_transition}
+	\caption{In all cases, blue lines represent the measured value of
+	the order parameter, black lines are average values calculated from
+	equilibrated Basin B systems at each temperature, green shaded regions
+	represent the standard deviation of each of the black line values, and 
+	red dashed lines show where the temperature is bumped to the next level.
+	(a) The pore spacing decreases smoothly as it approaches Basin B values.
+	(b) Membrane thickness increases steadily with temperature, however
+	it is still far from the Basin B value after 200 ns at 320K. (c) The
+	ratio of pore radius to is uncertainty rapidly decreases initially and
+	approaches the Basin B value smoothly until they finally overlap at 320K.}\label{fig:phase_transition}
 \end{figure}
@@
 	\end{subfigure}
-	\caption{}\label{fig:XRDrestrained}
+	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
+	with restraints placed on aromatic carbons shows all major features
+	present experimental WAXS. Near solid lines at constant z are a result of 
+	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
+	restrained parallel displaced configuration may also contained all
+	major experimental WAXS features. One can argue that R-spots is not present
+	but it is difficult to distinguish because of its intersection with the solid
+	R-helix line. Longer simulations are necessary to determine which structure
+	is the best match to experiment}\label{fig:XRDrestrained}
 \end{figure}
@@
 	\end{subfigure}
-	\caption{}\label{fig:XRDsim}
+	\caption{(a) All major features except R-helix are present in
+	XRD patterns resulting from an equilibrated sandwiched configuration 
+	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
+	(b) All major features execpt R-spots are present in XRD patterns 
+	resulting from an equilibrated parallel displaced configuration in Basin A.
+	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
+	are the only major features present in XRD patterns resulting from an 
+	equilibrated disordered phase}\label{fig:XRDsim}
 \end{figure}

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
Captions done for now!

@@
 	\end{subfigure}
-	\caption{}\label{fig:tail_packing}
+	\caption{(a) The trajectory can be stripped of all atoms except carbon
+	atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
+	still gives rise to R-spots. (c) Finding the center of mass and visualizing 
+	their coordinates reveals the hexagonal-like packing of the tails. (d) The 
+	distribution created by measuring the angle between each centroid (e.g. red 
+	in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
+	plane has distinct spikes near 30\degree, which is consistent with the location
+	of R-spots}\label{fig:tail_packing}
 \end{figure}

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
ionic conductivity update

@@
 uncertainty obtained using the Collective Diffusion model is much higher.
+Much longer simulations are needed to lower the uncertainty.
 For this reason we will likely only use the Nernst Einstein relation
-in future calculations of this type. It is evident that the ordered 
-phase has a higher ionic conductivity than the disordered phase. 
-Conductivity is enhanced in Phase A because the pores are more open,
-increasing the likelihood of site hopping. In all cases, our calculated values
-are higher than experimental values, as expected. The real system, 
-although mostly aligned and straight, still has a distribution of 
-azimuthal angles, lowering the effective ionic conductivity of the bulk 
+in future calculations of this type. Interestingly, Basin B 
+has a higher ionic conductivity than Basin A. Conductivity is enhanced in
+Basin B due to a higher sodium ion diffusivity. Transport of sodium is
+likely facilitated by the homgeneity of Basin B. Sodium ions have less
+sites to move to in Basin A. In all cases, our calculated values
+are higher than experimental values, as expected. Some of the 
+discrepancy is likely a result of using an imperfect forcefield. However, the real system, 
+although mostly aligned and straight, has a distribution of 
+azimuthal angles. This means that the pores have a degree of tortuosity 
+which lowers the effective ionic conductivity of the bulk 
 membrane. The ordering from isotropic to mostly aligned mesophases 
@@
 \hline
-Method & Phase A & Phase B \\
+Method & Basin A & Basin B \\
 \midrule
-Nernst Einstein & \num{8e-5} & \num{8e-5} \\
-Collective Diffusion & \num{6e-5} & \num{6e-5} \\
-Experiment & \num{1.3e-5} & \num{1.3e-5} \\
+Nernst Einstein & \num{(1.23$\pm$0.01)e-4} & \num{(1.76$\pm$0.02)e-4} \\
+Collective Diffusion & \num{(1.40$\pm$0.32)e-4} & \num{(4.6$\pm$2.4)e-4} \\
+Experiment & \num{(1.33$\pm$ 0.10)e-5} & -- \\
 \bottomrule
 \end{tabular}
-\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion agree within error.
-Both methods give calculated values of ionic conductivity which are higher, but reasonably close to experimental values~\label{table:conductivity}}
+\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
+agree within error. Both methods give calculated values of ionic conductivity which
+are an order of magnitude higher than experimental values~\label{table:conductivity}}
 %MRS2: I would say that they are reasonable close to experiment, though higher. Also somewhat contradicted in other places.

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
Added crosslinking results

@@
 \section*{Results and Discussion}
-
+\subsection*{Determination of system structural details}
 In order to construct an initial configuration which gives reliable 
@@
 
+\subsection{Ionic conductivity calculation}
+
 The model gives reasonable estimates of ionic conductivity for both phases.
@@
 likely facilitated by the homgeneity of Basin B. Sodium ions have less
-sites to move to in Basin A. In all cases, our calculated values
-are higher than experimental values, as expected. Some of the 
-discrepancy is likely a result of using an imperfect forcefield. However, the real system, 
-although mostly aligned and straight, has a distribution of 
-azimuthal angles. This means that the pores have a degree of tortuosity 
-which lowers the effective ionic conductivity of the bulk 
-membrane. The ordering from isotropic to mostly aligned mesophases 
-showed an 85 fold increase in ionic conductivity. We would expect additional
-gains in a perfect system.
+sites to move to in Basin A. Currently there is no experimental
+evidence of this trend, but it may be the subject of a future study. 
+In both cases, our calculated values for Basin A are higher than the 
+experimental values, as expected. Some of the discrepancy is likely a result
+of using an imperfect forcefield. However, the real system, although mostly
+aligned and straight, has a distribution of azimuthal angles, meaning 
+that the pores have a degree of tortuosity which lowers the effective 
+ionic conductivity of the bulk membrane. The ordering from isotropic to
+mostly aligned mesophases showed an 85 fold increase in ionic conductivity.
+We would expect additional gains in a perfect system.
 
@@
 agree within error. Both methods give calculated values of ionic conductivity which
-are an order of magnitude higher than experimental values~\label{table:conductivity}}
-%MRS2: I would say that they are reasonable close to experiment, though higher. Also somewhat contradicted in other places.
+are an order of magnitude higher than experimental values~\label{table:conductivity}}.
 \end{table}
+
+\subsection{Implementation of the crosslinking algorithm}
+
+We applied the crosslinking algorithm to an equilibrated structure in Basin B.
+The procedure will be repeated with Basin A in the near future.
+The resulting crosslinked structure has an even distribution of
+crosslinks between monomer tails of the same monomer, monomers stacked on  % table of values here
+top of each other and monomers in other pores, including across periodic
+boundaries. The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
+constant under a range of simulation conditions. Figure~\ref{fig:xlink} compares
+the pore behavior of a system that was a crosslinked and simulated for 10 ns to 
+the pore behavior of the same system taken just before crosslinking and run for 10 ns.
+Rather than plotting an average pore spacing, each pore-to-pore distance is plotted
+separately. Visually, one can tell that the crosslinked pores are locked in place. 
+The smaller pore spacing is also apparent by comparing the two plots. 
+The simulations discussed previously have not been crosslinked. Moving forward,
+the sandwiched system will be crosslinked in Basin A and used for
+transport studies.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{p2p_diagram.png}
+		\caption{}\label{fig:p2p_diagram}
+	\end{subfigure}
+		\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
+		\caption{}\label{fig:no_xlink_p2p}
+	\end{subfigure}
+		\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{xlink_p2p.png}
+		\caption{}\label{fig:xlink_p2p}
+	\end{subfigure}
+	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
+	Each numbered circle represents a pore. Distances are measured along each of the 
+	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
+	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
+	individual pores in the crosslinked system are stable relative to the uncrosslinked
+	system}\label{fig:xlink}
+\end{figure}

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/results.tex
edits

@@
 \centering
-\begin{tabular}{|c|c|c|}
+\begin{tabular}{ccc}
 \toprule
                    & \multicolumn{2}{c}{Starting Configuration} \\
+\hline
 Monomers per layer & Sandwiched & Parallel Displaced \\
@@
 
-The experimental 2D WAXS measurement contains five major reflections which
+Experimental WAXS measurements encode all structural details. 
+There are five major features present in the 2D experimental pattern which
 our model intends to reproduce (Figure~\ref{fig:WAXS}). The first is located
-at qz = 1.7 \angstrom \textsuperscript{-1}, corresponding to a real space 
-spacing of 3.7 \angstrom. The reflection is attributed to pi-pi stacking
+at qz = 1.7 \angstrom \textsuperscript{-1}, corresponding to a real spacing 
+of 3.7 \angstrom. The reflection is attributed to pi-pi stacking
 between aromatic rings in the direction perpendicular to the membrane plane, or z-axis. 
@@
 explained by the tilt angle of the alkane chains with respect to the xy plane. 
-The final major reflections correspond to the spacing and symmetry of the d100 
+The final major reflections correspond to the spacing and symmetry of the d\textsubscript{100} 
 plane which can be related to the distance between pores. The feature, which 
@@
 between the center of mass of each aromatic ring and the center of mass
-of all aromatic rings in respective pores. The pore radius is divided by
+of all aromatic rings in their respective pores. The pore radius is divided by
 its uncertainty in order to understand the degree to which monomers 
@@
 basins are in fact two different phases, we must observe evidence of a
-first order phase transition, which would be indicated by a discontinuity
+first order phase transition, which would be marked by a discontinuity
 in an order parameter as a function of temperature. Our 100 ns temperature
@@
 in aromatic ring spacing between experiment and simulation is likely a result
-of the inability of GAFF to properly handle aromatic interactions. The parallel
+of the inability of GAFF to properly handle aromatic interactions. The 
+sandwiched configuration shows R-spots in the expected location. A faint
+reflection is present in the location of R-helix. The parallel
 displaced configuration contains two lines of high intensity with maximum
@@
 constructive interference between the two features. The lines are located
-where one would expect to see R-helix. As the simulation is progressed, 
-the full line begins to fade and the reflection persists only at the 
-intersection with the R-alkanes. Most significantly, the line is no
-longer present where R-helix exists and, perhaps coincidentally, the 
+where one would expect to see R-helix and, perhaps coincidentally, the 
 intersection with R-alkanes occurs where one would expect to see R-spots.
+As the simulation is progressed, the full line begins to fade 
+(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
+where R-helix exists.
 
@@
 patterns produced from equilibrated MD trajectories shows the most consistency
-with the sandwiched conformation in Basin A. Systems were built in both the 
-parallel displaced and sandwiched conformations with an intial layer spacing of
+with the sandwiched configuration in Basin A. Systems were built in both the 
+parallel displaced and sandwiched configurations with an intial layer spacing of
 3.7 \angstrom. A third system was created by stacking layers in the sandwiched 
-conformation 5 \angstrom apart in order to guide it towards Basin B. For ease of
+configuration 5 \angstrom apart in order to guide it towards Basin B. For ease of
 reference, the third system will be referred to as the disordered system. The 
@@
 greater than 400 ns. Simulated diffration patterns were generated using 
-portions of the trajectory after equilibration (Figure~\ref{fig:XRDsim}). Equilibration was detected
+portions of the trajectory after equilibration. Equilibration was detected
 when the distance between pores and the membrane thickness stopped changing.
 Simulated diffraction patterns for all three structures are shown in 
-Fig~\ref{fig:XRDsim}. The equilibrated parallel displaced structure exhibits 
+Figure ~\ref{fig:XRDsim}. The equilibrated parallel displaced structure exhibits 
 R-alkanes and R-pores in the expected locations. Due to low resolution, making
 out the individual spots of R-pores is challenging and can be validated upon
-further inspection of the 3D structure factor. R-pi is also present, however it
-intersects R-alkanes because it is at a lower q than expected. This can be 
-explained by our model's inability to appropriately represent aromatic interactions.
+full spherical integration of the 3D structure factor. However, the same information
+can be extracted by measuring the pore spacing as described earlier. R-pi is
+also present, intersecting R-alkanes at a lower q value than in experiment.
 The rings prefer to stack $\approx 4.1 \angstrom$ apart as opposed to 3.7 \angstrom.
-R-helix and R-spots are both missing. The line which intersected both of these
+R-helix and R-spots are also both missing. The line which intersected both of these
 features in the restrained simulations faded upon equilibration which suggests
-that monomers in the parallel-displaced conformation may not give rise to the 
+that monomers in the parallel-displaced configuration may not give rise to the 
 experimental WAXS pattern seen. Simulated XRD of the sandwiched configuration 
@@
 expected location, which suggests that there is something intrinsic to
-the sandwiched packing which gives rise to such features. Finally, the 
-disordered structure exhibits R-alkanes and R-pores. R-helix and R-spots are not
-present. Given the evidence, the sandwiched configuration with layers spaced
+the sandwiched packing that gives rise to such features. Finally, the 
+disordered structure exhibits R-alkanes and R-pores but R-helix, R-pi and R-spots are not
+present. Given the evidence, the sandwiched configuration created with layers spaced
 3.7 \angstrom apart gives rise to an equilibrated structure closest to experiment.
@@
 showed that our system equilibrates to an average tilt angle close to zero 
-degrees (Fig~\ref{fig:tilt}). To understand the origin of the spots, we 
+degrees (Figure~\ref{fig:tilt}). To understand the origin of the spots, we 
 determined which atoms gave rise to the feature. By removing atoms from 
 the trajectory and simulating a diffraction pattern, we were able to isolate
-the cause of the spots to the tails. Since the tails are mostly flat, we
+the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}. Since the tails are mostly flat, we
 plotted the centroids of the tails and measured the angle between each centroid 
-and its nearest neighbors with respect to the plane of the membrane. The 
-distribution of these angles is consistent with the location of the spots.
+and its nearest neighbors with respect to the plane of the membrane (Figure~\ref{centroids}). The 
+distribution of these angles is consistent with the location of the spots (Figure~\ref{fig:angle_distribution}).
 We reason that monomer tails stacked closely in the sandwiched conformation
@@
 	\includegraphics[width=0.4\textwidth]{tilt.png}
-	\caption{The average angle between alkyl chains and the xy plane is nearly zero degrees}\label{fig:tilt}
+	\caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}
 \end{wrapfigure}
@@
 
-\subsection{Ionic conductivity calculation}
+\subsection*{Ionic conductivity calculation}
 
@@
 uncertainty obtained using the Collective Diffusion model is much higher.
-Much longer simulations are needed to lower the uncertainty.
+Much longer simulations are needed to lower the uncertainty. This is 
+especially true of the value calculated for Basin B using the collective
+diffusion model. The simulation was only run for 200 ns. Basin A collective
+diffusion calculations were generated from a 500 ns simulation. In both 
+cases, our calculated values would benefit from longer simulations. 
 For this reason we will likely only use the Nernst Einstein relation
@@
 Basin B due to a higher sodium ion diffusivity. Transport of sodium is
-likely facilitated by the homgeneity of Basin B. Sodium ions have less
+likely facilitated by the homogeneity of Basin B. Sodium ions have less
 sites to move to in Basin A. Currently there is no experimental
@@
 \midrule
-Nernst Einstein & \num{(1.23$\pm$0.01)e-4} & \num{(1.76$\pm$0.02)e-4} \\
-Collective Diffusion & \num{(1.40$\pm$0.32)e-4} & \num{(4.6$\pm$2.4)e-4} \\
-Experiment & \num{(1.33$\pm$ 0.10)e-5} & -- \\
+Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
+Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
+Experiment & \num{1.33e-5} (0.10) & -- \\
 \bottomrule
@@
 
-\subsection{Implementation of the crosslinking algorithm}
+\subsection*{Implementation of the crosslinking algorithm}
 
@@
 		\centering
-		\includegraphics[width=\textwidth]{p2p_diagram.png}
+		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
 		\caption{}\label{fig:p2p_diagram}

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/results.tex
formatting revisions

@@
 
-\begin{table}
+\begin{table}[H]
 \centering
@@
 \midrule
-4 & $3.71 \pm 0.08$ & $3.82 \pm 0.06$ \\
-5 & $3.99 \pm 0.08$ & $4.16 \pm 0.09$ \\
-6 & $4.83 \pm 0.08$ & $4.85 \pm 0.05$ \\
-7 & $4.73 \pm 0.06$ & $4.84 \pm 0.06$ \\
-8 & $5.08 \pm 0.08$ & $5.46 \pm 0.07$ \\
+4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
+5 & $3.99 \pm 0.04$ & $4.16 \pm 0.04$ \\
+6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
+7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
+8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
 \bottomrule
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
         \centering
-        \begin{subfigure}[b]{0.45\textwidth}
+        \begin{subfigure}[b]{0.475\textwidth}
                 \centering
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
+        \begin{subfigure}[b]{0.475\textwidth}
                 \centering
@@
 	\begin{subfigure}{0.475\textwidth}
+		\hspace{-1.2cm}
 		\centering
-		\includegraphics[width=\textwidth]{rzlayeredrestrained.png}
+		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
 		\caption{}\label{fig:rzplayeredrestrained}
@@
 	\begin{subfigure}{0.475\textwidth}
+		\hspace{-1.2cm}
 		\centering
-		\includegraphics[width=\textwidth]{rzoffsetrestrained.png}
+		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
 		\caption{}\label{fig:rzoffsetrestrained}
@@
 	with restraints placed on aromatic carbons shows all major features
-	present experimental WAXS. Near solid lines at constant z are a result of 
+	present in experimental WAXS. Near solid lines at constant z are a result of 
 	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
-	restrained parallel displaced configuration may also contained all
+	restrained parallel displaced configuration may also contain all
 	major experimental WAXS features. One can argue that R-spots is not present
@@
 		\centering
+		\hspace{-0.9cm}
 		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
@@
 		\centering
+		\hspace{-0.9cm}
 		\includegraphics[width=\textwidth]{offset_rzplot.png}
@@
 		\centering
+		\hspace{-0.9cm}
 		\includegraphics[width=\textwidth]{disorder_rzplot.png}
@@
 
+\begin{wrapfigure}{R}{0.4\textwidth}
+        \centering
+        \includegraphics[width=0.4\textwidth]{tilt.png}
+        \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}
+\end{wrapfigure}
+
 The spots that appear in the simulated XRD pattern of the sandwiched
@@
 the trajectory and simulating a diffraction pattern, we were able to isolate
-the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}. Since the tails are mostly flat, we
+the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the tails are mostly flat, we
 plotted the centroids of the tails and measured the angle between each centroid 
-and its nearest neighbors with respect to the plane of the membrane (Figure~\ref{centroids}). The 
+and its nearest neighbors with respect to the plane of the membrane (Figure~\ref{fig:centroids}). The 
 distribution of these angles is consistent with the location of the spots (Figure~\ref{fig:angle_distribution}).
@@
 
-\begin{wrapfigure}{R}{0.4\textwidth}
-	\centering
-	\includegraphics[width=0.4\textwidth]{tilt.png}
-	\caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}
-\end{wrapfigure}
-
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 		\centering
-		\includegraphics[width=\textwidth]{tails_topview.png}
+		\hspace{-1cm}
+		\vspace{1cm}
+		\includegraphics[width=\textwidth,scale=2]{tails_topview.png}
 		\caption{}\label{fig:tails_topview}
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/methods.tex
formatting revisions
edits

@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
-	\includegraphics[width=\linewidth]{build.PNG}
-	\caption{(a) Single monomers are parameterized and annealed to produce a low energy
+	\includegraphics[width=0.75\linewidth]{build.PNG}
+	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
 		configuration. (b) Monomers are rotated and assembled into layers with 
 		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
-		a pore. (d) Pores are duplicated and place in a monoclinic unit cell}\label{fig:python}
+		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
 \end{figure}
@@
 number of layers is preferred in order to reduce computational cost and 
-to allow us to look at longer timescales. Ultimately, we chose to build a system
-with 20 monomer layers in each pore in order to give sufficient
-resolution when simulating X-ray diffraction patterns.  % BJC: reword / mention xrd resolution - system size dependence in previous sentence
+to allow us to look at longer timescales. Ultimately, we chose to build a 
+system with 20 monomer layers in each pore in order to   
+obtain sufficient resolution when simulating X-ray diffraction patterns.
+This point will be explained in more detail later. 
+% BJC: reword / mention xrd resolution - system size dependence in previous sentence
 
@@
 which inspired separate systems starting with layer spacings greater than
- 4 \angstrom. Initial pore radius estimates of 0.6 nm were based on past TEM 
+ 4 \angstrom. We estimate the pore radius to be 0.6 nm based on past TEM 
 images and size exclusion rejection data\cite{feng_scalable_2014,
-feng_thin_2016,zhou_supported_2005}.
+feng_thin_2016,zhou_supported_2005}. Comparing a geometric
+measurement of pore size taken from an atomistic model, to a less
+precise, experimentally derived pore size estimate, will give ambiguous
+results. When constructing pores, we chose the carboxylate carbon from
+the monomer head group as a reference atom, and placed it a distance r from the
+pore center, where r is the pore radius. We will not make direct comparisons
+of pore radius between our model and experiment to avoid the ambiguity. 
 % There is plenty I can say about initial configuration. Starting layers
@@
 data as well as the various known stacking modes of benzene and substituted 
-benzene rings: sandwiched, parallel-displaced and T-shaped 
+benzene rings: sandwiched, parallel-displaced and T-shaped ~\cite{sinnokrot_estimates_2002}
 (\Cref{fig:sandwiched,fig:pd,fig:tshaped}). The T-shaped 
 configuration was ruled out based on the inconsistency of its $\approx$ 
-5 \angstrom equilibrium stacking distance. The system's preference
+5 \angstrom equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}. The system's preference
 towards the sandwiched vs. parallel displaced stacking modes was left
@@
 entropic differences based on the way the tails are able to pack.
-This difference may explain, in part, which stacking mode is more favorable.
+In the sandwiched configuration, all tails start out directly on top 
+of each other which may prevent closely stacked benzene rings. In the offset
+configuration, the tails in between each other which may allow layers
+to come together in a compact way. This difference may explain, in part,
+which stacking mode is more favorable.
 
-\begin{figure}
+\begin{figure}[ht]
 	\centering
@@
 		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{Sandwiched}\label{fig:sandwiched}
+		\caption{Sandwiched benzene dimers stack 3.8 \anstrom apart}\label{fig:sandwiched}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{PD.png}
-		\caption{Parallel-Displaced}\label{fig:pd}
+		\caption{Parallel-Displaced benzene dimers stack 3.4 \angstrom vertically and 1.6 \angstrom horizontally apart}\label{fig:pd}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{T-shaped}\label{fig:tshaped}
+		\caption{T-shaped benzene dimers stack 5.0 \angstrom apart}\label{fig:tshaped}
 	\end{subfigure}

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/methods.tex
polished

@@
 of each other which may prevent closely stacked benzene rings. In the offset
-configuration, the tails in between each other which may allow layers
+configuration, the tails are placed in between each other which may allow layers
 to come together in a compact way. This difference may explain, in part,
@@
 system dependence on initial monomer configuration. Restrained
-equilibrations are run in the NVT ensemble. Every 50 ps, force constants 
-are reduced by the square root of its previous value, starting from 
+equilibrations are run in the NVT ensemble. Every 50 ps, we reduce the force constants 
+by the square root of its previous value, starting from 
 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}. Once the force constant
@@
 %\end{itemize}
+
+Simulated X-ray diffraction patterns were generated based on atomic
+coordinates for a direct experimental comparison. All atomic coordinates
+were simulated as gaussian spheres of electron density corresponding to
+each atom's atomic number. A three dimensional fourier transform 
+(FT) of the array of electron density results in a three dimensional structure
+factor whicih represents the unit cell in reciprocal space. We perform an
+angular average of the structure factor about the z axis to generate a
+2D cross section close to what one would see experimentally. We matched 
+experimental 2D WAXS patterns by iterative improvement of our choice of 
+initial structure and equilibration procedure. 
+% Replace with a description written by Joe eventually
+
+Ionic conductivity was calculated using two different methods for
+robustness. The Nernst-Einstein relation relates 
+the DC ionic conductivity to ion diffusivity, $D$, concentration,
+$C$, ion charge, $q$, the boltzmann constant, $k_b$, and temperature,
+$T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$ Sodium ion diffusion 
+coefficients were found by calculating the slope of the linear
+region of the mean square displacement curve as indicated by the
+einstein relation \cite{einstein_investigations_1956}. Ion concentration
+was measured with respect to the entire unit cell. The second method, 
+termed the 'Collective Diffusion' model \cite{liu_collective_2013}, 
+measures the movement of the collective variable, Q, which is defined as
+the amount of charge transfer through the system. The diffusion 
+coefficient of Q, $D_Q$, can be calculated using the einstein relation.
+The conductance, $\gamma$ of the system can be calculated as:
+$$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
+achieved by multiplying by channel length and dividing by the membrane
+cross sectional area. A full derivation of the model can be accessed 
+elsewhere \cite{liu_collective_2013}.  
+% Talk about error somewhere?
 
@@
 constant under a range of simulation conditions.
-
-Simulated X-ray diffraction patterns were generated based on atomic
-coordinates to give a deeper understanding of the pore structure and
-spacing. All atomic coordinates were simulated as gaussian spheres of
-electron density  corresponding to each atom's atomic number. A three
-dimensional fourier transform (FT) of the array of electron density 
-results in a 3 dimensional structure factor representing the unit cell
-in reciprocal space. We perform an angular average of the structure factor
-about the z axis to generate a 2D cross section close to what one would see
-experimentally. We matched experimental 2D WAXS patterns by iterative
-improvement of our choice of initial structure and equilibration procedure. 
-% Replace with a description written by Joe eventually
-
-Ionic conductivity was calculated using two different methods for
-robustness. The Nernst-Einstein relation relates 
-the DC ionic conductivity to ion diffusivity, $D$, concentration,
-$C$, ion charge, $q$, the boltzmann constant, $k_b$, and temperature,
-$T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$ Sodium ion diffusion 
-coefficients were found by calculating the slope of the linear
-region of the mean square displacement curve as indicated by the
-einstein relation \cite{einstein_investigations_1956}. Ion concentration
-was measured with respect to the entire unit cell. The second method, 
-termed the 'Collective Diffusion' model \cite{liu_collective_2013}, 
-measures the movement of the collective variable, Q, which is defined as
-the amount of charge transfer through the system. The diffusion 
-coefficient of Q, $D_Q$, can be calculated using the einstein relation.
-The conductance, $\gamma$ of the system can be calculated as:
-$$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
-achieved by multiplying by channel length and dividing by the membrane
-cross sectional area. A full derivation of the model can be accessed 
-elsewhere \cite{liu_collective_2013}.  
-% Talk about error somewhere?

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/results.tex
polishing

@@
 spacing that is most consistent with the experimental value of 4.12 nm
-derived from SAXS measurements (Figure~\ref{fig:SAXS}). The remainder of
-this discussion will focus on the analysis of systems built with 5 
-monomers per layer. Pair correlation functions calculated between 
-aromatic rings along the length of the pores indicate that systems
-prefer to stay partitioned into layers (Fig~\ref{fig:zdf}).
+derived from SAXS measurements (Figure~\ref{fig:SAXS}). We verified 
+that the system stays partitioned into layers by plotting pair 
+correlation functions calculated between aromatic rings along the
+length of the pores (Fig~\ref{fig:zdf}).The remainder of this 
+discussion will focus on the analysis of systems built with 5
+monomers per layer.
 
@@
 4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
-5 & $3.99 \pm 0.04$ & $4.16 \pm 0.04$ \\
+5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
 6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
@@
 offset configuration. Systems built with 5 monomers per layer in a parallel
-displaced configuration results in a pore spacing closest to experimental
+displaced configuration result in a pore spacing closest to experimental
 data}\label{table:p2p} 
@@
 % There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
-
-Basin A and Basin B are two configurationally metastable basins. 
-We hesitate to classify the basins as separate phases. We hypothesize
-that Basin B is present at higher temperatures. This is evidenced by
-a simulation of a system in Basin A whose temperature was linearly
-ramped from 280K to 340K over 100 ns. Visually, there is a distinct
-change in pore structure from one characteristic of Basin A 
-(Figure~\ref{fig:280K_pore}) to one characteristic of Basin B 
-(Figure~\ref{fig:340K_pore}). To quantify our observation, we chose 
-three easily measurable order parameters: the distance between pores,
-the membrane the thickness and the ratio of pore radius to the uncertainty
-in pore radius. The distance between pores was measured as described 
-previously. The membrane thickness was measured using the length of the
-z box vector. The pore radius was measured by calculating the distance
-between the center of mass of each aromatic ring and the center of mass
-of all aromatic rings in their respective pores. The pore radius is divided by
-its uncertainty in order to understand the degree to which monomers 
-obstruct the pore region. Referring back to our temperature ramped system,
-the slope of all order parameters change around 315K - 325K 
-(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
-possibility of an abrupt change in system ordering. To prove that the 
-basins are in fact two different phases, we must observe evidence of a
-first order phase transition, which would be marked by a discontinuity
-in an order parameter as a function of temperature. Our 100 ns temperature
-ramp may have been too fast causing the system to suffer from hysteresis. To mitigate
-hysteresis, we performed a slow, stepwise temperature ramp. Starting from
-structures equilibrated at 280K, the system temperature was raised to 
-300K and allowed to equilibrate for 200 ns. At the end of 200 ns, the
-temperature was raised 5K and equilibrated again for 200 ns. We repeated
-this process until the system was equilibrated for 200 ns at 320K. In all
-cases, we observed smooth changes in order parameters as temperature was
-increased implying that we can not yet claim the existence of two phases (Figure~\ref{fig:phase_transition}).
-The same process will continue to be repeated up to 340K in the near future
-since we have not surpassed the temperatures where we observe abrupt slope 
-changes in pore spacing and membrane thickness (\Cref{fig:p2p_tramp,fig:thickness_tramp}).
-
-\begin{figure}
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:340K_pore}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_tramp.png}
-                \caption{}\label{fig:p2p_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_tramp.png}
-
-                \caption{}\label{fig:thickness_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_tramp.png}
-                \caption{}\label{fig:order_tramp}
-        \end{subfigure}
-        \caption{(a) The open pore structure exhibited by a structure equilibrated
-	at 280K is characteristic of Basin A. (b) The closed pore structure with 
-	a high degree of radial disorder exhibited when the structure in (a) is 
-	heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
-	vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs. 
-	temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
-	its uncertainty changes slope near 315K.}\label{fig:tramp}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_layered.png}
-		\caption{}\label{fig:p2p_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{thickness_layered.png}
-		\caption{}\label{fig:thickness_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{order_layered.png}
-		\caption{}\label{fig:order_layered}
-	\end{subfigure}
-	\caption{In all cases, blue lines represent the measured value of
-	the order parameter, black lines are average values calculated from
-	equilibrated Basin B systems at each temperature, green shaded regions
-	represent the standard deviation of each of the black line values, and 
-	red dashed lines show where the temperature is bumped to the next level.
-	(a) The pore spacing decreases smoothly as it approaches Basin B values.
-	(b) Membrane thickness increases steadily with temperature, however
-	it is still far from the Basin B value after 200 ns at 320K. (c) The
-	ratio of pore radius to is uncertainty rapidly decreases initially and
-	approaches the Basin B value smoothly until they finally overlap at 320K.}\label{fig:phase_transition}
-\end{figure}
 
@@
 \end{figure}
+
+Basin A and Basin B are two configurationally metastable basins. 
+We hesitate to classify the basins as separate phases. We hypothesize
+that Basin B is present at higher temperatures. This is evidenced by
+a simulation of a system in Basin A whose temperature was linearly
+ramped from 280K to 340K over 100 ns. Visually, there is a distinct
+change in pore structure from one characteristic of Basin A 
+(Figure~\ref{fig:280K_pore}) to one characteristic of Basin B 
+(Figure~\ref{fig:340K_pore}). To quantify our observation, we chose 
+three easily measurable order parameters: the distance between pores,
+the membrane the thickness and the ratio of pore radius to the uncertainty
+in pore radius. The distance between pores was measured as described 
+previously. The membrane thickness was measured using the length of the
+z box vector. The pore radius was measured by calculating the distance
+between the center of mass of each aromatic ring and the center of mass
+of all aromatic rings in their respective pores. The pore radius is divided by
+its uncertainty in order to understand the degree to which monomers 
+obstruct the pore region. Referring back to our temperature ramped system,
+the slope of all order parameters change around 315K - 325K 
+(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
+possibility of an abrupt change in system ordering. To prove that the 
+basins are in fact two different phases, we must observe evidence of a
+first order phase transition, which would be marked by a discontinuity
+in an order parameter as a function of temperature. Our 100 ns temperature
+ramp may have been too fast causing the system to suffer from hysteresis. To mitigate
+hysteresis, we performed a slow, stepwise temperature ramp. Starting from
+a sandwiched structure equilibrated at 280K, the system temperature was raised to 
+300K and allowed to equilibrate for 200 ns. At the end of 200 ns, the
+temperature was raised 5K and equilibrated again for 200 ns. We continued raising the 
+temperature by 5K and equilibrating for 200 ns until the system was 
+equilibrated for 200 ns at 320K. In all cases, we observed smooth changes
+in order parameters as temperature was increased implying that we can not yet
+claim the existence of two phases (Figure~\ref{fig:phase_transition}). The same
+process will continue to be repeated up to 340K in the near future since we have
+not surpassed the temperatures where we have observed the abrupt slope changes
+in pore spacing and membrane thickness (\Cref{fig:p2p_tramp,fig:thickness_tramp}).
+
+\begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+                \caption{}\label{fig:280K_pore}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{340K_tramp_close.png}
+                \caption{}\label{fig:340K_pore}
+        \end{subfigure}
+        \vskip\baselineskip
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{p2p_tramp.png}
+                \caption{}\label{fig:p2p_tramp}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{thickness_tramp.png}
+
+                \caption{}\label{fig:thickness_tramp}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{order_tramp.png}
+                \caption{}\label{fig:order_tramp}
+        \end{subfigure}
+        \caption{(a) The open pore structure exhibited by a structure equilibrated
+	at 280K is characteristic of Basin A. (b) The closed pore structure with 
+	a high degree of radial disorder exhibited when the structure in (a) is 
+	heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
+	vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs. 
+	temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
+	its uncertainty changes slope near 315K.}\label{fig:tramp}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{p2p_layered.png}
+		\caption{}\label{fig:p2p_layered}
+	\end{subfigure}
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{thickness_layered.png}
+		\caption{}\label{fig:thickness_layered}
+	\end{subfigure}
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{order_layered.png}
+		\caption{}\label{fig:order_layered}
+	\end{subfigure}
+	\caption{In all cases, blue lines represent the measured value of
+	the order parameter, black lines are average values calculated from
+	equilibrated Basin B systems at each temperature, green shaded regions
+	represent the standard deviation of each of the black line values, and 
+	red dashed lines show where the temperature is bumped to the next level.
+	(a) The pore spacing decreases smoothly as it approaches Basin B values.
+	(b) Membrane thickness increases steadily with temperature, however
+	it is still far from the Basin B value after 200 ns at 320K. (c) The
+	ratio of pore radius to is uncertainty rapidly decreases initially and
+	approaches the Basin B value smoothly until they finally overlap at 320K.}\label{fig:phase_transition}
+\end{figure}

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/methods.tex
updated captions

@@
 		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{Sandwiched benzene dimers stack 3.8 \anstrom apart}\label{fig:sandwiched}
+		\caption{}\label{fig:sandwiched}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{PD.png}
-		\caption{Parallel-Displaced benzene dimers stack 3.4 \angstrom vertically and 1.6 \angstrom horizontally apart}\label{fig:pd}
+		\caption{}\label{fig:pd}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{T-shaped benzene dimers stack 5.0 \angstrom apart}\label{fig:tshaped}
+		\caption{}\label{fig:tshaped}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{sandwichedlayers.png}
-		\caption{Two monomer layers stacked in the sandwiched configuration}\label{fig:sandwichedlayers}
+		\caption{}\label{fig:sandwichedlayers}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{offsetlayers.png}
-		\caption{Two monomer layers stacked in the parallel-displaced configuration}\label{fig:offsetlayers}
+		\caption{}\label{fig:offsetlayers}
 	\end{subfigure}
-	\caption{}\label{fig:stacking}
+	\caption{(a) Sandwiched benzene dimers stack 3.8 \anstrom apart. (b) Parallel-Displaced benzene dimers stack
+	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
+	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
+	configuration }\label{fig:stacking}
 \end{figure}

### 2017-08-28 Ben_Manuscripts/Paper1/Outline.tex
reverse outlining based on masters bypass paper

--- 2016-08-09 Ben_Manuscripts/Paper1/Outline.tex
@@
 \documentclass{article}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+\usepackage{subcaption}
+\usepackage{geometry}
+\geometry{legalpaper, margin=1in}
+\usepackage{amsmath} % or simply amstext
+\newcommand{\angstrom}{\textup{\AA}}
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-\author{Benjamin J. Coscia, Michael R. Shirts, Douglas L. Gin, Richard D. Noble}
+\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
 \begin{document}
   \bibliographystyle{ieeetr}
+  \graphicspath{{./figures/}}
   \maketitle
-\section{Introduction}
+  \section*{Introduction}
 
-Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
-\begin{itemize}
-	\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
-	\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
-	\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
-\end{itemize}
+  Nanostructured membrane materials have become increasingly popular for 
+  aqueous separations applications such as desalination and biorefinement
+  because they offer the ability to control membrane architecture at the
+  atomic scale allowing the design of solute-specific separation membranes
 
-Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
-\begin{itemize}
-	\item Leading technologies and their limitations:
-	\begin{itemize}
-		\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
-		\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
-		\item Zeolites - Good rejections/selectivities, but low flux and high cost of manufacturing. Generally limited to applications needing thermal/chemical resistance
-	\end{itemize}
-\end{itemize}
+  While RO and NF have seen many advances in the past few decades, they 
+  are far from perfect separation technologies.
 
-Lyotropic Liquid Crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques which may be feasible for large scale production.
-\begin{itemize}
-	\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
-	\item My monomer forms HII phase consisting of vertically aligned, monodisperse, straight pores in a hexagonal array
-	\item Hydrophilic regions point towards pore centers
-	\item Until recently, they could not be aligned - hindered progress
-	\item Talk about Yale alignment techniques
-	\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
-\end{itemize}
+  Nanostructured membranes can bypass many of the performance issues which
+  plague traditional NF and RO membranes.
 
-A molecular level understanding of solute transport in LLC membranes will accelerate development efforts by providing guidelines for monomer design.
-\begin{itemize}
-	\item HII phase studies currently limited mostly to one monomer with minor variations
-	\item Current optimization efforts performed through trial and error
-	\item Macroscopic models are the only source of predictive modeling
-	\item An atomistic understanding of the mechanism of solute transport can identify
-	performance bottle necks and direct design of future monomers/membranes
-	\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
-	\begin{itemize}
-		\item This could change how one thinks about molecules diffusing through membrane
-		\item Could also be a difference between lyotropic and thermotropic phases
-	\end{itemize}
-	\item Will we observe Donnan exclusion or some variation on it at the pore entrance
-	\item What are the relative weights of steric and electrical effects that deterimine selectivity -- is there an optimal balance 
-	\item How many monomers are in a layer?
-	\item What is the equilibrium water content in lyotropic phase?
-	\item We can vary the following to make predictions about new systems:
-	\begin{itemize}
-		\item Liquid crystal used - or a mixture of different liquid crystals
-		\item Minor structural variations (e.g. 7, 8, , 9, 10, 11 ... CH2's in the tails)
-		\item Counterion -- Size/valence of counterion
-		\item Functional head groups
-	\end{itemize}
-	\item How does varying these things effect pore separation, pore size, phase stability, and transport and why are these effects observed 
-\end{itemize}
+  Development of nanostructured materials has been limited by the ability
+  to synthesize and scale various fundamentally sound technologies.
 
-A physically accurate molecular model with easily modified structural features will launch a new phase of research into directing design of an optimal LLC membrane.
-\begin{itemize}
-	\item The paper will illustrate the development of a predictive molecular model
-	\item Measurements made to validate model
-	\item Observations of transport mechanism
-	\item The model is consistent with experiments and ready to extend to other systems
-\end{itemize}
+  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate
+  for aqueous separation applications.
 
-\section{System Setup}
+  A molecular level understanding of LLC membrane structure will elucidate
+  small molecule transport mechanisms, providing guidelines to reduce the
+  chemical space for the design of monomers used to create separation-specific
+  membranes.
 
-HII monomers were parameterized using the Generalized Amber Forcefield with the Antechamber package provided with AmberTools16. All molecular dynamics simulations were run using Gromacs version 5.1.2.
+  A clear picture of the nanoscopic LLC membrane structure, gained by building 
+  a molecular model will provide evidence to answer existing and newly proposed
+  questions.
 
-The most suitable monomer structural configuration was decided by applying a simulated annealing process to the parameterized monomer. 
-\begin{itemize}
-	\item Initially parameterized monomer gives unfavorable structure
-	\item Structure cooled from 1000 to 50 K over 10 nanoseconds
-	\item Result not global minimum but close enough for structure building
-	\item Multiple configurations saved from annealing trajectory to prove independence of starting config
-\end{itemize}
-
-The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable simulation length. 
-\begin{itemize}
-	\item Work done that shows coarse grain model self assembly in ~1000 ns
-	\item Attempts with HII system not fruitful
-	\item Wrote own code to assemble monomers into HII configuration (described in intro) close to what is expected -- equilibration simulations allow structure to relax into expected configuration 
-	\item Code has adjustable parameters: Pore-to-Pore distance, pore radius, number of monomer layers (justification for parameters chosen in following paragraphs)
-	\item This is the thermotropic phase, information used depends on thermotropic experimental data
-\end{itemize}
-
-After some experimentation, it was found that twenty monomer layers per pore provided a balance of structural accuracy and computational efficiency. 
-\begin{itemize}
-	\item Space between membrane layers in z direction - semi-isotropic sims fix z box dimension
-	\item Small number of layers create micellar structure
-	\item Beyond 20 layers is unnecessary to get expected configuration
-\end{itemize}
-
-The starting distance between layers was chosen so that energy minimization occured with no errors due to overlaps. 
-\begin{itemize}
-	\item Layers collapse to favorable layer-to-layer distance within first few picoseconds of equilibration 
-\end{itemize}
-
-\noindent The remaining parameters were chosen based on experimental data. 
-\begin{itemize}
-	\item SAXS to get Pore-to-Pore
-	\item TEM images estimate pore size
-\end{itemize}
-
-\noindent NPT simulations were run at 300 K and 1 bar for system equilibration. 
-\begin{itemize}
-	\item Monitored 'hexagonality'
-	\item Pores don't show perfect hexagonal character for short sims (~20 ns) 
-	\item We see a smaller average pore-to-pore distance than reported
-	\item Varied initial pore-to-pore distance and ran very long simulations
-	\item Starting pore-to-pore distances of 4.0 and 4.5 converge to same average with long\textbf{er} sims 
-\end{itemize}
-
-After an equilibrated structure was created, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
-\begin{itemize}
-	\item Crosslinking maintains alignment of cylindrical mesophases
-	\item head to tail addition
-	\item Details of crosslinking algorithm (refer to appendix or supplemental info)
-\end{itemize}
-
-\noindent The crosslinked system was then solvated with water to mimic a membrane in water.
-\begin{itemize}
-	\item x ns sims run to allow full water penetration into pores
-	\item simulated isotropically with enough water in between periodic images
-\end{itemize}
-
-\section{Results and Discussion}
-
-The final, equilibrated system had pores which were spaced 3.5 nm apart. This is the thermotropic phase though. More to come once system is solvated.
-
-Other things to be studied:
-\begin{itemize}
-	\item Monomers per layer
-	\begin{itemize}
-		\item Questions: How many monomers are in each layer? Do we observe pi stacking of benzene rings as hypothesized in papers? Are there even defined layers?
-		\item Hypothesis: There are an average of 7 monomers per layer when defined per unit volume but there are not well-defined layers as pictured in the literature.
-While long range order is maintained, hexagonal mesophases are disordered within their hydrophilic and hydrophobic domains.
-Staying completely ordered, stacked on top of each other is not entropically favorable.
-	\end{itemize}
-	\item Self diffusion of sodium in pores
-	\begin{itemize}
-		\item Past literature reports ions arranged in a circle about pore walls leaving void space as a pore. Simulation show that they may be arranged gaussian-like	
-		\item Ions may play a different role in transport than previously thought. They might hinder transport by slowing diffusion of other sodiums and molecules. 
-		\item Questions to be studied: Do sodium counter-ions stay bound to carbonyl groups?
-Do sodium ions that get through the membrane need to go all the way through or do they cause some sort of momentum transfer that pushes a different ion out of the pore on the opposite side?
-Is there ion diffusion through hydrophobic matrix?
-Is it negligible?
-What happens to the chlorine ion in NaCl?
-		\item Hypothesis: Sodium ions that are already acting as counterions stay mostly bound to their functional groups.
-Sodium ions diffusing through from bulk salt water need to diffuse all the way through and drag along a chlorine atom to maintain charge neutrality.
-Sodium ions tethered to chloride may exchange with sodium ions bound to monomer.
-There is negligible diffusion of sodium chloride through hydrophobic matrix.
-	\end{itemize}
-	\item Diffusion of water in pores
-	\begin{itemize}
-		\item Questions to be studied: How easily does water diffuse through the pores (permeability)?
-Is there diffusion at all through the hydrophobic matrix?
-If so, is it negligible?
-Is there a hydration shell around entering salt?
-Do waters get stripped from hydration shell?
-How does water interact with sodium ions?
-Is water transport faster down the center of the pore?
-Do water molecules orient themselves in a specific way at the pore walls?
-		\item Hypothesis: Water molecules will travel with through the pores with a parabolic laminar-like trajectory.
-Water molecules along the wall will be hindered as they get stuck in the hydrophilic head groups causing slower transport at the walls -- This hypothesis will depend on what I see once I solvate and equilibrate the system with water.
-I think the arrangement of sodium ions will change when solvated (That could be an intersting conclusion in itself).
-No water will be transported through hydrophobic regions.
-	\end{itemize}
-	\item Compare rates of diffusion of water and sodium to estimate selectivity and rejection
-	\begin{itemize}
-		\item I am studying this because they are the two parameters to be optimized ultimately
-	\end{itemize}
-\end{itemize}
-
-\section{Conclusion}
-
-In this work, a molecular model has been developed which can predict transport in an lyotropic liquid crystal membrane. 
-\begin{itemize}
-	\item Results presented for HII phase monomer but can be adapted to other LLCs
-	\item Model can be used for prediction of transport properties in new membranes
-\end{itemize}
-
-\end{document}
+  We must show that the developed molecular model is consistent with
+  physical observations so that we can rely on conclusions drawn about % better word for trust?
+  structural features characteristic of the system.

### 2017-08-28 Ben_Manuscripts/Paper1/Outline.tex
edits

@@
   because they offer the ability to control membrane architecture at the
-  atomic scale allowing the design of solute-specific separation membranes
+  atomic scale allowing the design of solute-specific separation membranes.
+  \begin{itemize}
+    \item Most membrane-based aqueous separations of small molecules can 
+    be achieved using reverse osmosis (RO) or nanofiltration (NF)
+  \end{itemize}
 
@@
   are far from perfect separation technologies.
+  \begin{itemize}
+    \textit{RO membranes}
+    \item \textbf{Inconsistent performance} : Current state-of-the-art RO membranes are unstructured with
+    tortuous and polydisperse diffusion pathways which leads to 
+    inconsistent performance
+    \item \textbf{High energy requirements} : Necessarily high feed pressures 
+    drive up energy requirements which strains developing regions and
+    contributes strongly to CO\textsubscript{2} emissions.
+    \item \textbf{Separation based on differences in solubility and diffusivity:
+    Moreover, designing RO membranes to achieve targeted separations of 
+    specific solutes is nearly impossible because various solutes dissolve
+    into and diffuse through the polymer matrix at different rates.
+    \item At best, one can exploit these differences to create a functional
+    selective barrier.
+    \textit{NF membranes}
+    \item NF was introduced as an intermediate between RO and ultrafiltration,
+    having the ability to separate organic matter and salts on the order of 
+    one nanometer in size.
+    \item Larger and well-defined pores drive down energy requirements while
+    still affording separation of solutes as small as ions to some degree
+    \item NF is often used as a precursor to reverse osmosis
+    \item Unfortunately, NF membranes, like RO, are produced with a pore size 
+    distribution which limits their ability to perform precise separations
+  \end{itemize}
 
@@
   plague traditional NF and RO membranes.
+  \begin{itemize}
+    \item \textbf{Tune size and functionality of building blocks} to control pore
+    size and shape: One can accomplish targeted separations with high 
+    selectivity by tuning shape, size and functionality of the molecular
+    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
+    \item As a result, solute rejecting pores can have their sizes tuned
+    uniformly, resulting in \textbf{strict size cut-offs}.
+    \item Entirely \textbf{different mechanisms} may govern transport in a given
+    nanostructured material which can inspire novel separation techniques.
+  \end{itemize}
 
@@
   to synthesize and scale various fundamentally sound technologies.
+  \begin{itemize}
+    \item \textbf{Graphene sheets} are atomically thick which results in excellent
+    permeability but defects during manufacturing severely impact 
+    selectivity.
+    \item Molecular dynamics simulations of \textbf{carbon nanotubes} show
+    promise but synthetic techniques are unable to achieve scalable alignment 
+    and pore monodispersity.
+    \item \textbf{Zeolites} have sub-nm pores with a narrow pore size 
+    distribution and MD simulations exhibit complete rejection of solvated ions,
+    however, experimental rejection was low and attributed to interstitial
+    defects formed during membrane synthesis
 

### 2017-08-28 Ben_Manuscripts/Paper1/Outline.tex
updates

@@
   because they offer the ability to control membrane architecture at the
-  atomic scale allowing the design of solute-specific separation membranes.
+  atomic scale allowing the design of solute-specific separation membranes. \cite{humplik_nanostructured_2011}
   \begin{itemize}
     \item Most membrane-based aqueous separations of small molecules can 
-    be achieved using reverse osmosis (RO) or nanofiltration (NF)
+    be achieved using reverse osmosis (RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}
   \end{itemize}
@@
     tortuous and polydisperse diffusion pathways which leads to 
-    inconsistent performance
+    inconsistent performance \cite{song_nano_2011}
     \item \textbf{High energy requirements} : Necessarily high feed pressures 
     drive up energy requirements which strains developing regions and
-    contributes strongly to CO\textsubscript{2} emissions.
+    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
     \item \textbf{Separation based on differences in solubility and diffusivity:
@@
     specific solutes is nearly impossible because various solutes dissolve
-    into and diffuse through the polymer matrix at different rates.
+    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
     \item At best, one can exploit these differences to create a functional
@@
     \item Larger and well-defined pores drive down energy requirements while
-    still affording separation of solutes as small as ions to some degree
+    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
     \item NF is often used as a precursor to reverse osmosis
     \item Unfortunately, NF membranes, like RO, are produced with a pore size 
-    distribution which limits their ability to perform precise separations
+    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
   \end{itemize}
@@
     permeability but defects during manufacturing severely impact 
-    selectivity.
+    selectivity. \cite{cohen-tanugi_multilayer_2016}
     \item Molecular dynamics simulations of \textbf{carbon nanotubes} show
-    promise but synthetic techniques are unable to achieve scalable alignment 
-    and pore monodispersity.
+    promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
+    unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
     \item \textbf{Zeolites} have sub-nm pores with a narrow pore size 
-    distribution and MD simulations exhibit complete rejection of solvated ions,
+    distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
     however, experimental rejection was low and attributed to interstitial
-    defects formed during membrane synthesis
+    defects formed during membrane synthesis \cite{li_desalination_2004}
+    \item There is a need for a scalable nanostructured membrane
+  \end{itemize}
 
-  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate
-  for aqueous separation applications.
+  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
+  aqueous separation applications. 
+  \begin{itemize}
+    \item LLCs share the characteristic ability of nanostructured membrane
+    materials to create \textbf{highly ordered structures} with the added benefits
+    of \textbf{low cost} and synthetic techniques feasible for 
+    \textbf{large scale production} \cite{feng_scalable_2014}
+    \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
+    phase. The presence of small amounts of water results in the H\textsubscript{II} 
+    phase.
+    \item In both cases, monomers assemble into mesophases made of hexagonally
+    packed, uniform size, cylinders with hydrophilic groups oriented inward
+    towards the pore center and hydrophobic groups facing outward.
+    \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
+    the monomer named Na-GA3C11 has been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
+    zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
+    \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
+    aligned, resulting in a low flux membrane, slowing research in the field.
+    \item In 2014, Feng et al. showed that the mesophases could be aligned 
+    using a magnetic field with subsequent crosslinking to lock the structure
+    in place \cite{feng_scalable_2014}
+    \item In 2016, Feng et al. showed that the same result could be obtained 
+    using a technique termed soft confinement \cite{feng_thin_2016}.
+    \item Following this breakthrough, research into LLC membranes has been
+    reinvigorated
+  \end{itemize}
+
+  A clear picture of the nanoscopic LLC membrane structure, gained by building 
+  a molecular model will provide evidence to answer existing and newly proposed
+  questions.
+    \begin{itemize}
+    \item We will limit our initial studies to studying assemblies formed by Na-GA3C11
+    \item We have also chosen to focus our initial efforts on the development of 
+    a model of the Col\textsubscript{h} phase membrane.
+    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
+    phase is a simpler starting point, due to the absence of water, and has
+    equivalent experimental structural data.
+    \item Despite the structural data, the
 
@@
   membranes.
-
-  A clear picture of the nanoscopic LLC membrane structure, gained by building 
-  a molecular model will provide evidence to answer existing and newly proposed
-  questions.
+    \begin{itemize}
+    \item LLCs are versatile and controllable with a \textbf{large chemical design
+    space} available for membrane design
+    \item It will be challenging to narrow down the design space and optimize 
+    solute-specific membranes
+    \item  We do not yet understand how to reduce the effective pore size or 
+    how to tune the chemical environment in the nanopores for effective water
+    desalination or small organic separations.
+    \item 
+    \end{itemize}
 

### 2017-08-28 Ben_Manuscripts/Paper1/Outline.tex
Reorganized intro

@@
     equivalent experimental structural data.
-    \item Despite the structural data, the
+    \item Despite having structural data, there is still information which 
+    experiment cannot definitively answer
+    \item The Col\textsubscript{h} phase is described as having pores made of
+    disks or layers stacked on top of one another, each containing a set 
+    number of monomers. A simple simulation study of a similar molecule suggests
+    that there are 4 monomers in each disk~\cite{zhu_methacrylated_2006}. A 
+    separate calculation based on the volume of the liquid crystal monomers proposes
+    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
+    A molecular model has the best chance of directly answering this question.
+    \item Once we know the number of monomers in each layer, we still do not know how 
+    monomers in each layer are positioned with respect to other layers. 
+    \item A driving force of self assembly in this system is thought to be pi-pi
+    stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
+    \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
+    advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
+    sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
+    \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
+    attraction which favors the parallel displaced configuration in all cases
+    except where the substitutions are extremely electron withdrawing
+    \cite{waller_hybrid_2006,ringer_effect_2006}.
+    \item While we might be able to provide answers to these questions using a 
+    molecular model, there remains the possibility that there is more than one 
+    metastable state associated with a given LLC system.
+    \item We must be able to identify which states can be produced experimentally
+    and what implications each state might have regarding transport properties.
+  \end{itemize}
 
-  A molecular level understanding of LLC membrane structure will elucidate
-  small molecule transport mechanisms, providing guidelines to reduce the
-  chemical space for the design of monomers used to create separation-specific
-  membranes.
+  A molecular level understanding of LLC membrane structure will provide guidelines
+  to reduce the large chemical space available to design monomers for creation of 
+  separation-specific membranes.
   \begin{itemize}
-    \item LLCs are versatile and controllable with a \textbf{large chemical design
-    space} available for membrane design
-    \item It will be challenging to narrow down the design space and optimize 
-    solute-specific membranes
+%     \item LLCs are versatile and controllable with a \textbf{large chemical design
+%     space} available for membrane design  %BJC: redundant
     \item  We do not yet understand how to reduce the effective pore size or 
@@
     desalination or small organic separations.
-    \item 
+    \item Rejection studies show that this membrane can not perform separations of
+    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
+    \item Over the past 20 years, LLC membrane studies have been limited primarily 
+    to Na-GA3C11 with some characterization done after minor structural modifications
+    \cite{resel_structural_2000}. 
+    \item Optimization has been performed through trial and error. The only source of 
+    predictive modeling has been macroscopic models which likely do not adequately describe 
+    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
+    \item It will be challenging to efficiently narrow down the design space in 
+    a laboratory setting.
+    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
+    structure which will be crucial to understanding the role of monomer structure in 
+    membrane design.
+    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
+    \item Choice of counterion may influence the establishment of a Donnan potential 
+    affecting the degree to which the membrane can exclude charged species.
+    \item Moieties inside the pores may interact with neutral solutes, rejecting
+    on the basis of shape and size, rather than just hydrodynamic radius.
+    \item  An atomistic understanding of pore structure and its influence on transport 
+    is necessary to identify performance bottle necks and direct design of future membranes. 
   \end{itemize}
@@
   structural features characteristic of the system.
+  \begin{itemize}
+    \item This article will illustrate the development of a predictive molecular model 
+    and the steps taken to ensure it mimics the real system within the constraints 
+    inherent to MD.
+    \item To understand how physically realistic the model is, validation by comparison
+    to experiment is necessary. We are primarily interested in reproducing the 
+    conclusions about structure which have been made from X-ray diffraction (XRD) 
+    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
+    \item We have comparied simulated X-ray diffraction patterns to experiment in 
+    order to match major features present in the 2D patterns.
+    \item We calculated ionic conductivity using two agreeing methods.
+    \item We examined the the influence of crosslinking on membrane structure.
+    \item We have created a model that can be used to probe the large design space
+    available for membrane design
+    \item The analysis used in this paper can be readily extended to the H\textsubscript{II}
+    phase and other similar LC systems.
+  \end{itemize}

### 2017-08-29 Ben_Manuscripts/Paper1/Outline.tex
Outlining methods

@@
   \end{itemize}
+
+  \section*{Methods}
+
+  HII monomers were parameterized using the Generalized AMBER Forcefield
+  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
+  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
+  assigned using tools from Openeye Scientific Software. All molecular dynamics 
+  simulations were run using the latest version of Gromacs 2016. 
+  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
+
+  An ensemble of characteristic, low-energy vacuum monomer configurations
+  were constructed by applying a simulated annealing process to a
+  parameterized monomer.
+  \begin{itemize}
+    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
+    \item A low energy configuration was pulled from the trajectory 
+    and charges were reassigned using the am1bccsym method of molcharge
+    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
+    \item Using the new charges, the monomer system was annealed again and monomer
+    configurations were pulled from the trajectory to be used for full
+    system construction (Figure~\ref{fig:python}a).
+  \end{itemize}
+
+  The timescale for self assembly of monomers into the hexagonal phase is
+  unknown and likely outside of a reasonable length for an atomistic
+  simulation, calling for a more efficient way to build the system. 
+  \begin{itemize}
+    \item Previous work has shown a coarse grain model self assemble into
+    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
+    \item We attempted atomistic self-assembly by packing monomers into a box 
+    using Packmol \cite{martinez_packmol:_2009}.
+    \item Simulations of greater than 100 ns show no indicators of progress 
+    towards an ordered system.
+    \item To bypass the slow self-assembly process, python scripts are used
+    to assemble monomers into a structure close to the expected equilibrium 
+    configuration (Figure~\ref{fig:python}).
+    \item A short, restrained equilibration, followed by NPT simulations 
+    between 400 and 500 ns, allows the initial configuration to relax into
+    an equilibrium configuration.
+    \item Our logic for choosing a starting configuration and the details 
+    of the equilibration schemes are presented below.
+  \end{itemize}
+
+  \begin{figure}[H]
+	\centering
+	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
+	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
+		configuration. (b) Monomers are rotated and assembled into layers with 
+		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
+		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
+  \end{figure}
+
+  A typical simulation volume contains four pores in a monoclinic unit cell,
+  the smallest unit cell that maintains hexagonal symmetry when extended 
+  periodically.
+  \begin{itemize}
+    \item Each pore is made of twenty stacked monomer layers with periodic 
+    continuity in the z direction, avoiding any edge effects and creating an 
+    infinite length pore ideal for studying transport.
+    \item A small number of layers is preferred in order to reduce computational
+    cost and to allow us to look at longer timescales.
+    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
+    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
+    This point will be explained in more detail later.
+  \end{itemize}
+
+  We chose initial guesses for the remaining structural parameters based on 
+  experimental data and treated them as variables during model development.
+  \begin{itemize}
+    \item The distance between pores was based on experimental SAXS data for
+    this system \cite{feng_thin_2016}.
+    \item The model's pores are spaced 4.5 nm apart initially, \approx 10 \% larger
+    than the experimental value in order to reduce unintended repulsions 
+    resulting from a tightly packed initial configuration.
+    \item The layer spacing is based on experimental 2D WAXS data.
+    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom apart.
+    \item It has been hypothesized that the features are a result of pi-pi
+    interactions between stacked aromatic rings \cite{feng_scalable_2014}.
+
+  An equilibration scheme with position restraints placed on aromatic rings
+  prevents unrealistic jumps during early equilibration steps.
+
+  Simulated X-ray diffraction patterns were generated based on atomic
+  coordinates for a direct experimental comparison.
+
+  \begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{sandwiched.png}
+		\caption{}\label{fig:sandwiched}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{PD.png}
+		\caption{}\label{fig:pd}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Tshaped.png}
+		\caption{}\label{fig:tshaped}
+	\end{subfigure}
+	\vskip\baselineskip
+	\begin{subfigure}[b]{0.475\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{sandwichedlayers.png}
+		\caption{}\label{fig:sandwichedlayers}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.475\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{offsetlayers.png}
+		\caption{}\label{fig:offsetlayers}
+	\end{subfigure}
+	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
+	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
+	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
+	configuration }\label{fig:stacking}
+  \end{figure}
+
+  Ionic conductivity was calculated using two different methods for
+  robustness.
+
+  Using an equilibrated structure, a crosslinking procedure was performed
+  in order to better parallel synthetic procedures.

### 2017-08-29 Ben_Manuscripts/Paper1/Outline.tex
organizing methods

@@
   experimental data and treated them as variables during model development.
+  %BJC: I could potentially break this paragraph into smaller paragraphs centered around
+  % the bolded structural parameters
   \begin{itemize}
-    \item The distance between pores was based on experimental SAXS data for
+    \item \textbf{The distance between pores} was based on experimental SAXS data for
     this system \cite{feng_thin_2016}.
-    \item The model's pores are spaced 4.5 nm apart initially, \approx 10 \% larger
-    than the experimental value in order to reduce unintended repulsions 
+    \item The model's pores are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
+    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
     resulting from a tightly packed initial configuration.
@@
     interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
+    \item Our simulations tend to equilibrate to a wider interlayer spacing of
+    $\approx$ 4.1 \angstrom, which inspired separate systems starting with layer 
+    spacings greater than 4 \angstrom.
+    \item We estimate the \textbf{pore radius} to be 0.6 nm based on past TEM images 
+    and size exclusion rejection data\cite{feng_scalable_2014,feng_thin_2016,
+    zhou_supported_2005}.
+    \item Comparing a geometric measurement of pore size derived from an 
+    atomistic model, to a less precise, experimentally derived pore size estimate,
+    will give ambiguous results.
+    \item What is meant by pore radius will not be clear until we have a clear picture
+    of the nanoscopic pore environment.
+    \item When constructing pores, we chose the carboxylate carbon from the monomer
+    head group as a reference atom, and placed it a distance r from the pore center,
+    where r is the pore radius.  %BJC: figure making that clear
+    \item We will not make direct comparisons of pore radius between our model 
+    and experiment to avoid the ambiguity. 
+    \item The \textbf{relative interlayer orientation} was chosen based on clues from 
+    diffraction data as well as the various known stacking modes of benzene 
+    and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
+    ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
+    \item The T-shaped configuration was ruled out based on the inconsistency of
+    its $\approx$ 5 \angstrom equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
+    \item The system's preference towards the sandwiched vs. parallel displaced 
+    stacking modes will be explored.
+    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
+    \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
+    suggests entropic differences based on the way the tails are able to pack.
+    \item In the sandwiched configuration, all tails start out directly on top
+    of each other which may prevent closely stacked benzene rings.
+    \item In the offset configuration, the tails are placed in between each other 
+    which may allow layers to come together in a compact way.
+    \item This difference may explain, in part, which stacking mode is more favorable.
+  \end{itemize}
 

### 2017-08-29 Ben_Manuscripts/Paper1/Outline.tex
Methods finished outlining for now

@@
   prevents unrealistic jumps during early equilibration steps.
+  \begin{itemize}
+    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
+    configurations while allowing monomer tails to settle.
+    \item Doing so also mitigates system dependence on initial monomer configuration.
+    \item Restrained equilibrations are run in the NVT ensemble.
+    \item Every 50 ps, we reduce the force constants by the square root of its 
+    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
+    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
+    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
+    restraining potential.  %BJC: I can reference an equilibration script that can be released with the supplemental info or something
+    \item The resulting unrestrained structure is allowed to equilibrate in the NPT
+    ensemble for 400 - 500 ns.
+  \end{itemize}
 
+  %BJC: the following paragraph will be replaced with something that Joe writes
   Simulated X-ray diffraction patterns were generated based on atomic
   coordinates for a direct experimental comparison.
+  \begin{itemize}
+    \item All atomic coordinates were simulated as gaussian spheres of electron
+    density corresponding to each atom's atomic number.
+    \item A three dimensional fourier transform (FT) of the array of electron 
+    density results in a three dimensional structure factor which represents
+    the unit cell in reciprocal space.
+    \item We perform an angular average of the structure factor about the 
+    z axis to generate a 2D cross section close to what one would see 
+    experimentally.
+    \item We matched experimental 2D WAXS patterns by iterative improvement
+    of our choice of initial structure and equilibration procedure.
+  \end{itemize}
 
@@
   robustness.
+  \begin{itemize}
+    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
+    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
+    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
+    \item Sodium ion diffusion coefficients were found by calculating the slope
+    of the linear region of the mean square displacement curve as indicated by
+    the einstein relation \cite{einstein_investigations_1956}.]
+    \item Ion concentration was measured with respect to the entire unit cell. %BJC: I don't think this needs to be said
+    \item The second method, termed the 'Collective Diffusion' model, measures 
+    the movement of the collective variable, Q, which is defined as the amount
+    of charge transfer through the system.
+    \item The diffusion coefficient of Q, $D_Q$, can be calculated using the 
+    einstein relation.
+    \item The conductance, $\gamma$ of the system can be calculated as:
+    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
+    achieved by multiplying by channel length and dividing by the membrane
+    cross sectional area.
+    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
+  \end{itemize}
 
@@
   in order to better parallel synthetic procedures. 
+  \begin{itemize}
+    \item The purpose of crosslinking is to maintain macroscopic alignment of 
+    the crystalline domains, ensuring aligned, hexagonally packed pores.
+    \item For that reason, we are not concerned with replicating the kinetics 
+    of the reaction, but instead emphasize the consistency of the final structure
+    with experimental structural data.
+    \item The algorithm was developed based on the known reaction mechanism.
+    \item Crosslinking of this system is a free radical polymerization (FRP)
+    taking place between terminal vinyl groups present on each of the three
+    monomer tails.
+    \item FRPs require an initiator which bonds to the system, meaning new atoms
+    were introduced into the system.
+    \item For simplicity, the initiator was simulated as hydrogen and made present 
+    in the simulation by including them in all possible bonding positions as dummy atoms.
+    \item The crosslinking procedure is carried out iteratively.
+    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
+    \item The topology is updated with new bonds and dummy hydrogen atoms are 
+    changed to appropriate hydrogen types. 
+    \item Head-to-tail addition was the only propagation mode considered due to 
+    its dominance the real system.
+    \item Direction of attack was not considered because the resultant mixture 
+    is racemic.
+    %BJC: The following items belongs in results/discussion
+    \item The resulting crosslinked structure has an even distribution of
+    crosslinks between monomer tails of the same monomer, monomers stacked on
+    top of each other and monomers in other pores, including across periodic
+    boundaries.
+    \item The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
+    constant under a range of simulation conditions.
+  \end{itemize}

### 2017-08-29 Ben_Manuscripts/Paper1/Outline.tex
added results

@@
     this system \cite{feng_thin_2016}.
-    \item The model's pores are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
+    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
     than the experimental value of 4.12 nm in order to reduce unintended repulsions 
     resulting from a tightly packed initial configuration.
-    \item The layer spacing is based on experimental 2D WAXS data.
+    \item To calculate the equilibrated pore spacing, we measured the distance between pore
+    centers.
+    \item Pore centers were located by averaging the coordinates of sodium ions in their 
+    respective pores.
+    \item Statistics were generated using the bootstrapping technique.
+    \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
+    sampling from the original trajectory
+    % This might be too much detail. Maybe leave excess detail for 
+    \item We are interested in 5 pore-to-pore distances which should all be equal in 
+    a perfect hexagonal array. Only 4 are independent  %BJC: small figure here for clarity? supplemental info?
+    \item Each pore spacing has its own trajectory with its own average value
+    \item The average value of each pore spacing is averaged to get the overall
+    average pore spacing. 
+    \item The standard deviation of average values is reported as the uncertainty in pore spacing.
+    \item The \textbf{layer spacing} is based on experimental 2D WAXS data.
     \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom apart.
@@
   \end{itemize}
+
+  \section*{Results and Discussion}
+
+  \subsection*{Determination of Nanoscopic Structural Details}
+
+  In order to construct an initial configuration which gives reliable 
+  trends, we need to understand the composition of layers, how far apart
+  to stack the layers, and how to orient them with respect to each other.
+  \begin{itemize}
+  	\item To verify our choices for each parameter, we compare our calculations
+	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
+	scattering (WAXS), and ionic conductivity measurements.
+  \end{itemize}
+
+  To discern the composition of the monomer layers, we ran simulations of 
+  systems created with 4 - 8 monomers per layer.
+  \begin{itemize}
+  	\item Both the sandwiched and parallel displaced configurations were tested.
+	\item All systems remained stable for at least 50 ns.
+	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
+	Systems built with 5 monomers in each layer equilibrate to a pore spacing
+	that is most consistent with the experimental value of 4.12 nm derived from
+	SAXS measurements (Figure~\ref{fig:SAXS}).
+	\item We verified that the system stays partitioned into layers by plotting 
+	pair correlation functions calculated between aromatic rings along the length
+	of the pores (Fig~\ref{fig:zdf}).
+	\item The remainder of this discussion will focus on the analysis of systems
+	built with 5 monomers per layer. 
+  \end{itemize}
+
+  \begin{table}[H]
+  \centering
+  \begin{tabular}{ccc}
+  \toprule
+  		   & \multicolumn{2}{c}{Starting Configuration} \\
+  \hline
+  Monomers per layer & Sandwiched & Parallel Displaced \\
+  \midrule
+  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
+  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
+  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
+  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
+  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
+  \bottomrule
+  \end{tabular}
+  \caption{The pore spacing of the model increases as number of monomers
+  in each layer increases. The pore spacing of a system starting in the 
+  sandwiched configuration is systematically lower than that started in an 
+  offset configuration. Systems built with 5 monomers per layer in a parallel
+  displaced configuration result in a pore spacing closest to experimental
+  data}\label{table:p2p} 
+  \end{table}
+
+  \begin{figure}[h]
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{zdf5layered.png}
+		\caption{}\label{fig:zdf_layered}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{zdf5offset.png}
+		\caption{}\label{fig:zdf_offset}
+	\end{subfigure}
+	\caption{Pair distribution functions of aromatic carbons for the
+	(a) 5 monomer per layer, sanwiched and (b) 5 monomer per layer, 
+	parallel displaced configurations. Spikes in the distribution mark
+	distinct layers. The magnitude of the spikes with respect to the 
+	average suggest that the 5 monomer per layer, sandwiched configuration
+	possesses the highest degree of layer partitioning.}\label{fig:zdf}
+  \end{figure}
+
+  The initial distance between layers can influence the approach towards
+  equilibrium.
+
+  Experimental WAXS measurements encode all structural details.
+
+  \begin{figure}[ht]
+	\centering
+	\begin{subfigure}[t]{0.47\linewidth}
+		\centering
+		\raisebox{.2\textwidth}{%
+		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
+		}
+		\caption{}\label{fig:WAXS}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.43\linewidth}
+		\centering
+	%	\vspace{12mm}
+		\includegraphics[width=\linewidth]{SAXS.png}
+		\caption{}\label{fig:SAXS}
+	\end{subfigure}
+	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
+	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
+	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
+  \end{figure}
+
+  We varied the relative interlayer orientation between sandwiched and 
+  parallel-displaced based on our knowledge of the stability of these two
+  pi-stacking modes.
+
+  \begin{figure}
+	\centering
+	\begin{subfigure}{0.475\textwidth}
+		\hspace{-1.2cm}
+		\centering
+		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
+		\caption{}\label{fig:rzplayeredrestrained}
+	\end{subfigure}
+	\begin{subfigure}{0.475\textwidth}
+		\hspace{-1.2cm}
+		\centering
+		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
+		\caption{}\label{fig:rzoffsetrestrained}
+	\end{subfigure}
+	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
+	with restraints placed on aromatic carbons shows all major features
+	present in experimental WAXS. Near solid lines at constant z are a result of 
+	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
+	restrained parallel displaced configuration may also contain all
+	major experimental WAXS features. One can argue that R-spots is not present
+	but it is difficult to distinguish because of its intersection with the solid
+	R-helix line. Longer simulations are necessary to determine which structure
+	is the best match to experiment}\label{fig:XRDrestrained}
+  \end{figure}
+
+  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
+  patterns produced from equilibrated MD trajectories shows the most consistency
+  with the sandwiched configuration in Basin A.
+
+  \begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.31\textwidth}
+		\centering
+		\hspace{-0.9cm}
+		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
+		\caption{}\label{fig:sandwich_rzplot}
+	\end{subfigure}
+	\begin{subfigure}{0.31\textwidth}
+		\centering
+		\hspace{-0.9cm}
+		\includegraphics[width=\textwidth]{offset_rzplot.png}
+		\caption{}\label{fig:offsetrzplot}
+	\end{subfigure}
+	\begin{subfigure}{0.31\textwidth}
+		\centering
+		\hspace{-0.9cm}
+		\includegraphics[width=\textwidth]{disorder_rzplot.png}
+		\caption{}\label{fig:disorder_rzplot.png}
+	\end{subfigure}
+	\caption{(a) All major features except R-helix are present in
+	XRD patterns resulting from an equilibrated sandwiched configuration 
+	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
+	(b) All major features execpt R-spots are present in XRD patterns 
+	resulting from an equilibrated parallel displaced configuration in Basin A.
+	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
+	are the only major features present in XRD patterns resulting from an 
+	equilibrated disordered phase}\label{fig:XRDsim}
+  \end{figure}
+
+  \begin{wrapfigure}{R}{0.4\textwidth}
+        \centering
+        \includegraphics[width=0.4\textwidth]{tilt.png}
+        \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}
+  \end{wrapfigure}
+
+  The spots that appear in the simulated XRD pattern of the sandwiched
+  conformation are a result of the way alkane tails pack together.
+
+  \begin{figure}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\hspace{-1cm}
+		\vspace{1cm}
+		\includegraphics[width=\textwidth,scale=2]{tails_topview.png}
+		\caption{}\label{fig:tails_topview}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{tails_rzplot.png}
+		\caption{}\label{fig:tails_rzplot}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{centroids_box.png}
+		\caption{}\label{fig:centroids}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{angles_traj_layered.png}
+		\caption{}\label{fig:angle_distribution}
+	\end{subfigure}
+	\caption{(a) The trajectory can be stripped of all atoms except carbon
+	atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
+	still gives rise to R-spots. (c) Finding the center of mass and visualizing 
+	their coordinates reveals the hexagonal-like packing of the tails. (d) The 
+	distribution created by measuring the angle between each centroid (e.g. red 
+	in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
+	plane has distinct spikes near 30\degree, which is consistent with the location
+	of R-spots}\label{fig:tail_packing}
+  \end{figure}
+
+  Basin A and Basin B are two configurationally metastable basins.
+
+  \begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+                \caption{}\label{fig:280K_pore}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{340K_tramp_close.png}
+                \caption{}\label{fig:340K_pore}
+        \end{subfigure}
+        \vskip\baselineskip
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{p2p_tramp.png}
+                \caption{}\label{fig:p2p_tramp}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{thickness_tramp.png}
+
+                \caption{}\label{fig:thickness_tramp}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{order_tramp.png}
+                \caption{}\label{fig:order_tramp}
+        \end{subfigure}
+        \caption{(a) The open pore structure exhibited by a structure equilibrated
+	at 280K is characteristic of Basin A. (b) The closed pore structure with 
+	a high degree of radial disorder exhibited when the structure in (a) is 
+	heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
+	vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs. 
+	temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
+	its uncertainty changes slope near 315K.}\label{fig:tramp}
+  \end{figure}
+
+  \begin{figure}
+	\centering
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{p2p_layered.png}
+		\caption{}\label{fig:p2p_layered}
+	\end{subfigure}
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{thickness_layered.png}
+		\caption{}\label{fig:thickness_layered}
+	\end{subfigure}
+	\begin{subfigure}{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{order_layered.png}
+		\caption{}\label{fig:order_layered}
+	\end{subfigure}
+	\caption{In all cases, blue lines represent the measured value of
+	the order parameter, black lines are average values calculated from
+	equilibrated Basin B systems at each temperature, green shaded regions
+	represent the standard deviation of each of the black line values, and 
+	red dashed lines show where the temperature is bumped to the next level.
+	(a) The pore spacing decreases smoothly as it approaches Basin B values.
+	(b) Membrane thickness increases steadily with temperature, however
+	it is still far from the Basin B value after 200 ns at 320K. (c) The
+	ratio of pore radius to is uncertainty rapidly decreases initially and
+	approaches the Basin B value smoothly until they finally overlap at 320K.}\label{fig:phase_transition}
+  \end{figure}
+
+  \subsection*{Ionic conductivity calculation}
+
+  The model gives reasonable estimates of ionic conductivity for both phases.
+
+  \begin{table}[H]
+  \centering
+  \begin{tabular}{ccc}
+  \toprule
+  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
+  \hline
+  Method & Basin A & Basin B \\
+  \midrule
+  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
+  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
+  Experiment & \num{1.33e-5} (0.10) & -- \\
+  \bottomrule
+  \end{tabular}
+  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
+  agree within error. Both methods give calculated values of ionic conductivity which
+  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
+  \end{table}
+
+  \subsection*{Implementation of the crosslinking algorithm}
+
+  We applied the crosslinking algorithm to an equilibrated structure in Basin B.
+
+  \begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
+		\caption{}\label{fig:p2p_diagram}
+	\end{subfigure}
+		\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
+		\caption{}\label{fig:no_xlink_p2p}
+	\end{subfigure}
+		\begin{subfigure}{0.31\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{xlink_p2p.png}
+		\caption{}\label{fig:xlink_p2p}
+	\end{subfigure}
+	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
+	Each numbered circle represents a pore. Distances are measured along each of the 
+	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
+	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
+	individual pores in the crosslinked system are stable relative to the uncrosslinked
+	system}\label{fig:xlink}
+  \end{figure}

### 2017-08-29 Ben_Manuscripts/Paper1/Outline.tex
results updated

@@
     and experiment to avoid the ambiguity. 
+    \item However, we do define a pore radius based for our own purposes.
+    \item Pore radius was measured by calculating the distance between the center of 
+    mass of each aromatic ring and the center of mass of all aromatic rings in their 
+    respective pores.
     \item The \textbf{relative interlayer orientation} was chosen based on clues from 
@@
 	\caption{Pair distribution functions of aromatic carbons for the
-	(a) 5 monomer per layer, sanwiched and (b) 5 monomer per layer, 
+	(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, 
 	parallel displaced configurations. Spikes in the distribution mark
@@
 	average suggest that the 5 monomer per layer, sandwiched configuration
-	possesses the highest degree of layer partitioning.}\label{fig:zdf}
+	possesses a higher degree of layer partitioning.}\label{fig:zdf}
   \end{figure}
 
-  The initial distance between layers can influence the approach towards
-  equilibrium.
-
   Experimental WAXS measurements encode all structural details. 
+  \begin{itemize}
+  	\item There are five major features present in the 2D experimental 
+	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
+	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
+	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
+	attributed to pi-pi stacking between aromatic rings in the direction
+	perpendicular to the membrane plane, or z-axis. For simplicity, this 
+	reflection will be referred to as R-pi.
+	\item A weak intensity line is located at exactly half the qz value of
+	R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
+	real space periodic spacing of 7.4 \angstrom. This reflection has been 
+	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
+	along the z axis meaning if the positions of the aromatic rings can
+	be traced by a helix, then for each turn in the helix, there should be
+	two aromatic rings. For this reason it will be referred to as R-helix.
+	\item A third major reflection is marked by a low intensity ring located
+	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
+	corresponds to 4.5 \angstrom which is characteristic of the average 
+	spacing between packed alkane chains. This reflection will be called R-alkanes.
+	\item Within R-alkanes, are four spots of higher intensity which 
+	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
+	in their respective quadrants. In many liquid crystal systems this can be
+	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
+	\item The final major reflections correspond to the spacing and symmetry of 
+	the d\textsubscript{100} plane which can be related to the distance between
+	pores. The feature, which will be called R-pores, is characterized by dots 
+	along qz = 0. The spacing between dots is indicative of the hexagonal 
+	symmetry of the packed pores. It is easiest to interpret the data by 
+	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
+  \end{itemize}
 
@@
 
+  The initial distance between layers can influence the approach towards
+  equilibrium. 
+  \begin{itemize}
+  	\item Equilibrated systems built according to the 3.7 \angstrom 
+	layer spacing implied by R-pi are characterized by a defined, cylindrical and
+	open pore structure.
+	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
+	\item We will refer to this system as Basin A (Figure~\ref{fig:280K_pore}).
+	\item Simulations of systems built with layers stacked greater than 4 
+	\angstrom apart results in a pore structure characterized by high radial 
+	disorder, while still maintaining partitioning between hydrophobic and 
+	hydrophilic regions.
+	\item This will be called Basin B (Figure~\ref{fig:340K_pore}).
+	\item It is apparent that this LLC membrane may exist in at least two metastable states.
+	\item The distinct difference in pore structure exhibited by each phase will 
+	likely lead to different transport mechanisms.
+	\item Understanding which phase exists experimentally is necessary in order
+	to appropriately study the system.
+  \end{itemize}
+
   We varied the relative interlayer orientation between sandwiched and 
-  parallel-displaced based on our knowledge of the stability of these two
+  parallel-displaced based on our knowledge of the stability of the two
   pi-stacking modes.
+  \begin{itemize}
+  	\item We generated simulated X-ray diffraction patterns from the highly
+	restrained initial configurations created during equilibration
+	\item The patterns establish a difference between the two stacking 
+	modes (Figure~\ref{fig:XRDrestrained}).
+	\item In each pattern, R-alkanes is present at a distance of $\approx
+	1.5$ \angstrom \textsuperscript{-1} (4.2 \angstrom in real space).
+  	\item R-pi is also present in each pattern, although it appears to 
+	intersect R-alkanes because the spacing between aromatic rings is 
+	similar to the alkane chain packing.
+	\item The difference in aromatic ring spacing between experiment and
+	simulation is likely a result of the inability of GAFF to properly handle
+	aromatic interactions.
+	\item The sandwiched configuration shows R-spots in the expected location.
+	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
+	\item The parallel displaced configuration contains two lines of high 
+	intensity with maximum intensity occurring where they intersect the alkane
+	chain region due to constructive interference between the two features.
+	\item The lines are located where one would expect to see R-helix and, 
+	perhaps coincidentally, the intersection with R-alkanes occurs where one 
+	would expect to see R-spots.
+	%BJC: might save the following sentence for equilibrium trajectories
+	\item As the simulation is progressed, the full line begins to fade 
+	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
+	where R-helix exists.
+  \end{itemize}
 
@@
   with the sandwiched configuration in Basin A.
+  \begin{itemize}
+  	\item Systems were built in both the parallel displaced and sandwiched 
+	configurations with an intial layer spacing of 3.7 \angstrom.
+	\item A third system was created by stacking layers in the sandwiched 
+	configuration 5 \angstrom apart in order to guide it towards Basin B.
+	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
+	\item For ease of reference, the third system will be referred to as the disordered system. %BJC: omit and call it basin B
+	\item The three systems were equilibrated according to our procedure with
+	NPT simulations of greater than 400 ns.
+	\item Simulated diffration patterns were generated using portions of the
+	trajectory after equilibration.
+	\item Equilibration was detected when the distance between pores and the 
+	membrane thickness stopped changing.
+	\item Simulated diffraction patterns for all three structures are shown in 
+	Figure ~\ref{fig:XRDsim}. 
+	%BJC: maybe break into a separate paragraph starting here
+	\item The equilibrated parallel displaced structure exhibits R-alkanes and
+	R-pores in the expected locations. 
+	\item Due to low resolution, making out the individual spots of R-pores is
+	challenging and can be validated upon full spherical integration of the 3D 
+	structure factor. However, the same information can be extracted by measuring 
+	the pore spacing as described earlier.
+	\item R-pi is also present, intersecting R-alkanes at a lower q value than
+	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
+	opposed to 3.7 \angstrom.
+	\item R-helix and R-spots are also both missing.
+	\item The line which intersected both of these features in the restrained 
+	simulations faded upon equilibration which suggests that monomers in the 
+	parallel-displaced configuration may not give rise to the experimental WAXS 
+	pattern seen.
+	\item Simulated XRD of the sandwiched configuration contains all features 
+	except for R-helix.
+	\item Most notably, R-spots appears in the expected location, which suggests 
+	that there is something intrinsic to the sandwiched packing that gives rise 
+	to such features. 
+	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
+	R-helix, R-pi and R-spots are not present.
+  \end{itemize}
 
@@
   conformation are a result of the way alkane tails pack together.
+  \begin{itemize}
+  	\item Previously, the spots in the diffraction pattern had been explained 
+	as the product of tilted alkane chains.
+	\item We measured the tilt angle of the alkane chains and showed that our 
+	system equilibrates to an average tilt angle close to zero degrees (Figure~\ref{fig:tilt}). 
+	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.
+	\item By removing atoms from the trajectory and simulating a diffraction 
+	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
+	\item Since the tails are mostly flat, we plotted the centroids of the 
+	tails and measured the angle between each centroid and its nearest neighbors
+	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
+	\item The distribution of these angles is consistent with the location of 
+	the spots (Figure~\ref{fig:angle_distribution}).
+	\item We reason that monomer tails stacked closely in the sandwiched conformation
+	are forced to splay apart and pack in between in each other which creates a
+	nearly hexagonal array of packed tails. 
+  \end{itemize}
 
@@
   Basin A and Basin B are two configurationally metastable basins.
+  \begin{itemize}
+  	\item We hesitate to classify the basins as separate phases.
+	\item We hypothesize that Basin B is present at higher temperatures.
+	\item This is evidenced by a simulation of a system in Basin A whose temperature
+	was linearly ramped from 280K to 340K over 100 ns.
+	\item Visually, there is a distinct change in pore structure from one
+	characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of 
+	Basin B (Figure~\ref{fig:340K_pore}).
+	\item To quantify our observation, we chose three easily measurable order 
+	parameters: the distance between pores, the membrane thickness and the
+	ratio of pore radius to the uncertainty in pore radius.
+	\item The pore radius is divided by its uncertainty in order to understand
+	the degree to which monomers obstruct the pore region.
+	\item Referring back to our temperature ramped system, the slope of all 
+	order parameters change around 315K - 325K 
+	(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
+	possibility of an abrupt change in system ordering.
+	\item To prove that the basins are in fact two different phases, we must 
+	observe evidence of a first order phase transition, which would be marked 
+	by a discontinuity in an order parameter as a function of temperature.
+	\item Our 100 ns temperature ramp may have been too fast causing the system
+	to suffer from hysteresis.
+	%BJC: should this go in methods?
+	\item To mitigate hysteresis, we performed a slow, stepwise temperature ramp.
+	\item Starting from a sandwiched structure equilibrated at 280K, the system
+	temperature was raised to 300K and allowed to equilibrate for 200 ns.
+	\item At the end of 200 ns, the temperature was raised 5K and equilibrated 
+	again for 200 ns.
+	\item We continued raising the temperature by 5K and equilibrating for 200 ns
+	until the system was equilibrated for 200 ns at 320K.
+	\item In all cases, we observed smooth changes in order parameters as temperature
+	was increased implying that we can not yet claim the existence of two phases 
+	(Figure~\ref{fig:phase_transition}).
+	\item I have this run out to about 335K right now. I have to see if there is anything
+	noteworthy to report
 
@@
   The model gives reasonable estimates of ionic conductivity for both phases.
+  \begin{itemize}
+  	\item Calculated values of ionic conductivity obtained using the Nernst 
+	Einstein relation and Collective Diffusion model are compared in 
+	Table~\ref{table:conductivity}.
+	\item The two methods agree with each other within error, although the 
+	uncertainty obtained using the Collective Diffusion model is much higher.
+	\item Much longer simulations are needed to lower the uncertainty.
+	\item  This is especially true of the value calculated for Basin B using
+	the collective diffusion model. % TODO: Run Basin B out longer
+	\item Basin A collective diffusion calculations were generated from a 
+	500 ns simulation.
+	\item In both cases, our calculated values would benefit from longer simulations. 
+	\item For this reason we will likely only use the Nernst Einstein relation
+	in future calculations of this type. 
+	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
+	\item Conductivity is enhanced in Basin B due to a higher sodium ion diffusivity.
+	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
+	Sodium ions have less ites to move to in Basin A.
+	\item No experimental evidence of this trend. May Xunda will find something
+	\item In both cases, our calculated values for Basin A are higher than the 
+	experimental values, as expected. 
+	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
+	\item However, the real system, although mostly aligned and straight, has a 
+	distribution of azimuthal angles, meaning that the pores have a degree of 
+	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
+	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
+	fold increase in ionic conductivity. We would expect additional gains in a 
+	perfectly aligned system.
+  \end{itemize}
 
@@
 
-  We applied the crosslinking algorithm to an equilibrated structure in Basin B.
-
+  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
+  Basin A.
+  \begin{itemize}  %BJC: working on the following
+  	\item Distribution of crosslinks
+	\item Pore spacing
+	\item X-ray diffraction
+	\item Ionic Conductivity
+  \end{itemize}
+  %BJC: THe following figure will be replaced with one representative of the new
+  % data I am  collecting above.
   \begin{figure}[H]

### 2017-08-30 Ben_Manuscripts/Paper1/Outline.tex
minor updates

@@
 
-  Experimental WAXS measurements encode all structural details. 
+  Experimental WAXS measurements encode all remaining structural details. 
+  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
   \begin{itemize}
@@
 	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
-	\item We will refer to this system as Basin A (Figure~\ref{fig:280K_pore}).
+	\item We will refer to this system as Basin A (Figure~\ref{fig:abasin}).
 	\item Simulations of systems built with layers stacked greater than 4 
@@
 	hydrophilic regions.
-	\item This will be called Basin B (Figure~\ref{fig:340K_pore}).
+	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
 	\item It is apparent that this LLC membrane may exist in at least two metastable states.
@@
   \end{itemize}
+
+  \begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+                \caption{}\label{fig:abasin}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{340K_tramp_close.png}
+                \caption{}\label{fig:bbasin}
+        \end{subfigure}
+	\caption{From a qualitative standpoint, Basin A (a) is characterized by a
+	hollow cylindrical pore while pores in Basin B (b) are characterized by a
+	higher degree of radial disorder}\label{fig:basins}
+  \end{figure}
 
@@
 
-  The model gives reasonable estimates of ionic conductivity for both phases.
+  The model gives reasonable estimates of ionic conductivity when compared to 
+  experiment.
   \begin{itemize}
@@
 	uncertainty obtained using the Collective Diffusion model is much higher.
-	\item Much longer simulations are needed to lower the uncertainty.
-	\item  This is especially true of the value calculated for Basin B using
-	the collective diffusion model. % TODO: Run Basin B out longer
-	\item Basin A collective diffusion calculations were generated from a 
-	500 ns simulation.
-	\item In both cases, our calculated values would benefit from longer simulations. 
+	\item Much longer simulations are needed to lower the uncertainty. % TODO: Run Basin B out longer at same conditions as A
+	\item Collective diffusion calculations were generated from 
+	500 ns simulations.
+	\item Our calculated values would benefit from longer simulations. 
 	\item For this reason we will likely only use the Nernst Einstein relation
@@
 	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
-	\item Conductivity is enhanced in Basin B due to a higher sodium ion diffusivity.
+	\item We hypothesize that conductivity is enhanced in Basin B due to a 
+	higher sodium ion diffusivity.
 	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
-	Sodium ions have less ites to move to in Basin A.
-	\item No experimental evidence of this trend. May Xunda will find something
+	Sodium ions have less sites to move to in Basin A.
+	\item There is currently no experimental evidence of this trend. Maybe Xund will find something
 	\item In both cases, our calculated values for Basin A are higher than the 
@@
   Basin A.
-  \begin{itemize}  %BJC: working on the following
-  	\item Distribution of crosslinks
-	\item Pore spacing
-	\item X-ray diffraction
-	\item Ionic Conductivity
+  \begin{itemize}  %BJC: working on the following. The following is what I expect
+  	\item There is an even distribution of crosslinks between same monomer tails, 
+	between monomers in the same pore and between monomers in different pores 
+	including periodic boundaries.
+	\item The distance between pores shrinks by 1 \angstrom after the system is 
+	crosslinked
+	\item Major features are still present in the X-ray diffraction
+	\item The ionic conductivity is higher/lower in the crosslinked system
   \end{itemize}

### 2017-08-30 Ben_Manuscripts/Paper1/Outline.tex
outlining phase transition section

@@
 \usepackage{subcaption}
-\usepackage{geometry}
-\geometry{legalpaper, margin=1in}
+\usepackage[margin=1in]{geometry}
 \usepackage{amsmath} % or simply amstext
+\usepackage{siunitx}
+\usepackage{booktabs}
+\usepackage[export]{adjustbox}
 \newcommand{\angstrom}{\textup{\AA}}
+\usepackage{cleveref}
+\usepackage{booktabs}
+\usepackage{gensymb}
+\usepackage{float}
 \title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
@@
   \begin{itemize}
-    \textit{RO membranes}
+    \item \textit{RO membranes}
     \item \textbf{Inconsistent performance} : Current state-of-the-art RO membranes are unstructured with
@@
     contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
-    \item \textbf{Separation based on differences in solubility and diffusivity:
+    \item \textbf{Separation based on differences in solubility and diffusivity}:
     Moreover, designing RO membranes to achieve targeted separations of 
@@
     selective barrier.
-    \textit{NF membranes}
+    \item \textit{NF membranes}
     \item NF was introduced as an intermediate between RO and ultrafiltration,
@@
 
-  \begin{figure}[H]
+  \begin{figure}[h]
 	\centering
@@
 
-  \begin{table}[H]
+  \begin{table}[h]
   \centering
@@
 	noteworthy to report	
+  \end{itemize}
 
@@
   % data I am  collecting above.
-  \begin{figure}[H]
+  \begin{figure}[h]
 	\centering
@@
   \end{figure}
+\end{document}

### 2017-08-31 Ben_Manuscripts/Paper1/basins.tex
Outline of section about metastable basins

--- 2017-08-29 Ben_Manuscripts/Paper1/Outline.tex
@@
 \usepackage{subcaption}
-\usepackage{geometry}
-\geometry{legalpaper, margin=1in}
+\usepackage[margin=1in]{geometry}
 \usepackage{amsmath} % or simply amstext
+\usepackage{siunitx}
+\usepackage{booktabs}
+\usepackage[export]{adjustbox}
 \newcommand{\angstrom}{\textup{\AA}}
-\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
+\usepackage{cleveref}
+\usepackage{booktabs}
+\usepackage{gensymb}
+\usepackage{float}
+
 \begin{document}
-  \bibliographystyle{ieeetr}
   \graphicspath{{./figures/}}
-  \maketitle
-  \section*{Introduction}
-
-  Nanostructured membrane materials have become increasingly popular for 
-  aqueous separations applications such as desalination and biorefinement
-  because they offer the ability to control membrane architecture at the
-  atomic scale allowing the design of solute-specific separation membranes. \cite{humplik_nanostructured_2011}
+  We can not immediately classify Basin A and Basin B as separate phases.
   \begin{itemize}
-    \item Most membrane-based aqueous separations of small molecules can 
-    be achieved using reverse osmosis (RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}
+	\item To prove the existence of two phases we need evidence of a
+	a first order phase transition.
+	\item A first order phase transition can be denoted by a discontinuity
+        of some order parameter in response to an external condition such as
+	temperature.
+	\item We chose three easily measurable order parameters: the distance
+	between pores, the membrane thickness and the ratio of pore radius to
+	the uncertainty in pore radius.
+        \item The pore radius is divided by its uncertainty as a way of quantifying
+        the degree to which monomers obstruct the pore region.
   \end{itemize}
 
-  While RO and NF have seen many advances in the past few decades, they 
-  are far from perfect separation technologies.
+  Basin B is the dominant configuration at higher temperatures.
   \begin{itemize}
-    \textit{RO membranes}
-    \item \textbf{Inconsistent performance} : Current state-of-the-art RO membranes are unstructured with
-    tortuous and polydisperse diffusion pathways which leads to 
-    inconsistent performance \cite{song_nano_2011}
-    \item \textbf{High energy requirements} : Necessarily high feed pressures 
-    drive up energy requirements which strains developing regions and
-    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
-    \item \textbf{Separation based on differences in solubility and diffusivity:
-    Moreover, designing RO membranes to achieve targeted separations of 
-    specific solutes is nearly impossible because various solutes dissolve
-    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
-    \item At best, one can exploit these differences to create a functional
-    selective barrier.
-    \textit{NF membranes}
-    \item NF was introduced as an intermediate between RO and ultrafiltration,
-    having the ability to separate organic matter and salts on the order of 
-    one nanometer in size.
-    \item Larger and well-defined pores drive down energy requirements while
-    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
-    \item NF is often used as a precursor to reverse osmosis
-    \item Unfortunately, NF membranes, like RO, are produced with a pore size 
-    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
-  \end{itemize}
-
-  Nanostructured membranes can bypass many of the performance issues which
-  plague traditional NF and RO membranes.
-  \begin{itemize}
-    \item \textbf{Tune size and functionality of building blocks} to control pore
-    size and shape: One can accomplish targeted separations with high 
-    selectivity by tuning shape, size and functionality of the molecular
-    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
-    \item As a result, solute rejecting pores can have their sizes tuned
-    uniformly, resulting in \textbf{strict size cut-offs}.
-    \item Entirely \textbf{different mechanisms} may govern transport in a given
-    nanostructured material which can inspire novel separation techniques.
-  \end{itemize}
-
-  Development of nanostructured materials has been limited by the ability
-  to synthesize and scale various fundamentally sound technologies.
-  \begin{itemize}
-    \item \textbf{Graphene sheets} are atomically thick which results in excellent
-    permeability but defects during manufacturing severely impact 
-    selectivity. \cite{cohen-tanugi_multilayer_2016}
-    \item Molecular dynamics simulations of \textbf{carbon nanotubes} show
-    promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
-    unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
-    \item \textbf{Zeolites} have sub-nm pores with a narrow pore size 
-    distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
-    however, experimental rejection was low and attributed to interstitial
-    defects formed during membrane synthesis \cite{li_desalination_2004}
-    \item There is a need for a scalable nanostructured membrane
-  \end{itemize}
-
-  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
-  aqueous separation applications. 
-  \begin{itemize}
-    \item LLCs share the characteristic ability of nanostructured membrane
-    materials to create \textbf{highly ordered structures} with the added benefits
-    of \textbf{low cost} and synthetic techniques feasible for 
-    \textbf{large scale production} \cite{feng_scalable_2014}
-    \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-    phase. The presence of small amounts of water results in the H\textsubscript{II} 
-    phase.
-    \item In both cases, monomers assemble into mesophases made of hexagonally
-    packed, uniform size, cylinders with hydrophilic groups oriented inward
-    towards the pore center and hydrophobic groups facing outward.
-    \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
-    the monomer named Na-GA3C11 has been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
-    zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
-    \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
-    aligned, resulting in a low flux membrane, slowing research in the field.
-    \item In 2014, Feng et al. showed that the mesophases could be aligned 
-    using a magnetic field with subsequent crosslinking to lock the structure
-    in place \cite{feng_scalable_2014}
-    \item In 2016, Feng et al. showed that the same result could be obtained 
-    using a technique termed soft confinement \cite{feng_thin_2016}.
-    \item Following this breakthrough, research into LLC membranes has been
-    reinvigorated
-  \end{itemize}
-
-  A clear picture of the nanoscopic LLC membrane structure, gained by building 
-  a molecular model will provide evidence to answer existing and newly proposed
-  questions.
-  \begin{itemize}
-    \item We will limit our initial studies to studying assemblies formed by Na-GA3C11
-    \item We have also chosen to focus our initial efforts on the development of 
-    a model of the Col\textsubscript{h} phase membrane.
-    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-    phase is a simpler starting point, due to the absence of water, and has
-    equivalent experimental structural data.
-    \item Despite having structural data, there is still information which 
-    experiment cannot definitively answer
-    \item The Col\textsubscript{h} phase is described as having pores made of
-    disks or layers stacked on top of one another, each containing a set 
-    number of monomers. A simple simulation study of a similar molecule suggests
-    that there are 4 monomers in each disk~\cite{zhu_methacrylated_2006}. A 
-    separate calculation based on the volume of the liquid crystal monomers proposes
-    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-    A molecular model has the best chance of directly answering this question.
-    \item Once we know the number of monomers in each layer, we still do not know how 
-    monomers in each layer are positioned with respect to other layers. 
-    \item A driving force of self assembly in this system is thought to be pi-pi
-    stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
-    \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
-    advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
-    sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
-    \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
-    attraction which favors the parallel displaced configuration in all cases
-    except where the substitutions are extremely electron withdrawing
-    \cite{waller_hybrid_2006,ringer_effect_2006}.
-    \item While we might be able to provide answers to these questions using a 
-    molecular model, there remains the possibility that there is more than one 
-    metastable state associated with a given LLC system.
-    \item We must be able to identify which states can be produced experimentally
-    and what implications each state might have regarding transport properties.
-  \end{itemize}
-
-  A molecular level understanding of LLC membrane structure will provide guidelines
-  to reduce the large chemical space available to design monomers for creation of 
-  separation-specific membranes.
-  \begin{itemize}
-%     \item LLCs are versatile and controllable with a \textbf{large chemical design
-%     space} available for membrane design  %BJC: redundant
-    \item  We do not yet understand how to reduce the effective pore size or 
-    how to tune the chemical environment in the nanopores for effective water
-    desalination or small organic separations.
-    \item Rejection studies show that this membrane can not perform separations of
-    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
-    \item Over the past 20 years, LLC membrane studies have been limited primarily 
-    to Na-GA3C11 with some characterization done after minor structural modifications
-    \cite{resel_structural_2000}. 
-    \item Optimization has been performed through trial and error. The only source of 
-    predictive modeling has been macroscopic models which likely do not adequately describe 
-    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
-    \item It will be challenging to efficiently narrow down the design space in 
-    a laboratory setting.
-    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
-    structure which will be crucial to understanding the role of monomer structure in 
-    membrane design.
-    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
-    \item Choice of counterion may influence the establishment of a Donnan potential 
-    affecting the degree to which the membrane can exclude charged species.
-    \item Moieties inside the pores may interact with neutral solutes, rejecting
-    on the basis of shape and size, rather than just hydrodynamic radius.
-    \item  An atomistic understanding of pore structure and its influence on transport 
-    is necessary to identify performance bottle necks and direct design of future membranes. 
-  \end{itemize}
-
-  We must show that the developed molecular model is consistent with
-  physical observations so that we can rely on conclusions drawn about % better word for trust?
-  structural features characteristic of the system.
-  \begin{itemize}
-    \item This article will illustrate the development of a predictive molecular model 
-    and the steps taken to ensure it mimics the real system within the constraints 
-    inherent to MD.
-    \item To understand how physically realistic the model is, validation by comparison
-    to experiment is necessary. We are primarily interested in reproducing the 
-    conclusions about structure which have been made from X-ray diffraction (XRD) 
-    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
-    \item We have comparied simulated X-ray diffraction patterns to experiment in 
-    order to match major features present in the 2D patterns.
-    \item We calculated ionic conductivity using two agreeing methods.
-    \item We examined the the influence of crosslinking on membrane structure.
-    \item We have created a model that can be used to probe the large design space
-    available for membrane design
-    \item The analysis used in this paper can be readily extended to the H\textsubscript{II}
-    phase and other similar LC systems.
-  \end{itemize}
-
-  \section*{Methods}
-
-  HII monomers were parameterized using the Generalized AMBER Forcefield
-  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
-  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
-  assigned using tools from Openeye Scientific Software. All molecular dynamics 
-  simulations were run using the latest version of Gromacs 2016. 
-  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-
-  An ensemble of characteristic, low-energy vacuum monomer configurations
-  were constructed by applying a simulated annealing process to a
-  parameterized monomer.
-  \begin{itemize}
-    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
-    \item A low energy configuration was pulled from the trajectory 
-    and charges were reassigned using the am1bccsym method of molcharge
-    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
-    \item Using the new charges, the monomer system was annealed again and monomer
-    configurations were pulled from the trajectory to be used for full
-    system construction (Figure~\ref{fig:python}a).
-  \end{itemize}
-
-  The timescale for self assembly of monomers into the hexagonal phase is
-  unknown and likely outside of a reasonable length for an atomistic
-  simulation, calling for a more efficient way to build the system. 
-  \begin{itemize}
-    \item Previous work has shown a coarse grain model self assemble into
-    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
-    \item We attempted atomistic self-assembly by packing monomers into a box 
-    using Packmol \cite{martinez_packmol:_2009}.
-    \item Simulations of greater than 100 ns show no indicators of progress 
-    towards an ordered system.
-    \item To bypass the slow self-assembly process, python scripts are used
-    to assemble monomers into a structure close to the expected equilibrium 
-    configuration (Figure~\ref{fig:python}).
-    \item A short, restrained equilibration, followed by NPT simulations 
-    between 400 and 500 ns, allows the initial configuration to relax into
-    an equilibrium configuration.
-    \item Our logic for choosing a starting configuration and the details 
-    of the equilibration schemes are presented below.
-  \end{itemize}
-
-  \begin{figure}[H]
-	\centering
-	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
-	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
-		configuration. (b) Monomers are rotated and assembled into layers with 
-		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
-		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
-  \end{figure}
-
-  A typical simulation volume contains four pores in a monoclinic unit cell,
-  the smallest unit cell that maintains hexagonal symmetry when extended 
-  periodically.
-  \begin{itemize}
-    \item Each pore is made of twenty stacked monomer layers with periodic 
-    continuity in the z direction, avoiding any edge effects and creating an 
-    infinite length pore ideal for studying transport.
-    \item A small number of layers is preferred in order to reduce computational
-    cost and to allow us to look at longer timescales.
-    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
-    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
-    This point will be explained in more detail later.
-  \end{itemize}
-
-  We chose initial guesses for the remaining structural parameters based on 
-  experimental data and treated them as variables during model development.
-  %BJC: I could potentially break this paragraph into smaller paragraphs centered around
-  % the bolded structural parameters
-  \begin{itemize}
-    \item \textbf{The distance between pores} was based on experimental SAXS data for
-    this system \cite{feng_thin_2016}.
-    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
-    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
-    resulting from a tightly packed initial configuration.
-    \item To calculate the equilibrated pore spacing, we measured the distance between pore
-    centers.
-    \item Pore centers were located by averaging the coordinates of sodium ions in their 
-    respective pores.
-    \item Statistics were generated using the bootstrapping technique.
-    \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
-    sampling from the original trajectory
-    % This might be too much detail. Maybe leave excess detail for 
-    \item We are interested in 5 pore-to-pore distances which should all be equal in 
-    a perfect hexagonal array. Only 4 are independent  %BJC: small figure here for clarity? supplemental info?
-    \item Each pore spacing has its own trajectory with its own average value
-    \item The average value of each pore spacing is averaged to get the overall
-    average pore spacing. 
-    \item The standard deviation of average values is reported as the uncertainty in pore spacing.
-    \item The \textbf{layer spacing} is based on experimental 2D WAXS data.
-    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom apart.
-    \item It has been hypothesized that the features are a result of pi-pi
-    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
-    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-    $\approx$ 4.1 \angstrom, which inspired separate systems starting with layer 
-    spacings greater than 4 \angstrom.
-    \item We estimate the \textbf{pore radius} to be 0.6 nm based on past TEM images 
-    and size exclusion rejection data\cite{feng_scalable_2014,feng_thin_2016,
-    zhou_supported_2005}.
-    \item Comparing a geometric measurement of pore size derived from an 
-    atomistic model, to a less precise, experimentally derived pore size estimate,
-    will give ambiguous results.
-    \item What is meant by pore radius will not be clear until we have a clear picture
-    of the nanoscopic pore environment.
-    \item When constructing pores, we chose the carboxylate carbon from the monomer
-    head group as a reference atom, and placed it a distance r from the pore center,
-    where r is the pore radius.  %BJC: figure making that clear
-    \item We will not make direct comparisons of pore radius between our model 
-    and experiment to avoid the ambiguity. 
-    \item However, we do define a pore radius based for our own purposes.
-    \item Pore radius was measured by calculating the distance between the center of 
-    mass of each aromatic ring and the center of mass of all aromatic rings in their 
-    respective pores.
-    \item The \textbf{relative interlayer orientation} was chosen based on clues from 
-    diffraction data as well as the various known stacking modes of benzene 
-    and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
-    ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
-    \item The T-shaped configuration was ruled out based on the inconsistency of
-    its $\approx$ 5 \angstrom equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
-    \item The system's preference towards the sandwiched vs. parallel displaced 
-    stacking modes will be explored.
-    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
-    \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
-    suggests entropic differences based on the way the tails are able to pack.
-    \item In the sandwiched configuration, all tails start out directly on top
-    of each other which may prevent closely stacked benzene rings.
-    \item In the offset configuration, the tails are placed in between each other 
-    which may allow layers to come together in a compact way.
-    \item This difference may explain, in part, which stacking mode is more favorable.
-  \end{itemize}
-
-  An equilibration scheme with position restraints placed on aromatic rings
-  prevents unrealistic jumps during early equilibration steps.
-  \begin{itemize}
-    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-    configurations while allowing monomer tails to settle.
-    \item Doing so also mitigates system dependence on initial monomer configuration.
-    \item Restrained equilibrations are run in the NVT ensemble.
-    \item Every 50 ps, we reduce the force constants by the square root of its 
-    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
-    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
-    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
-    restraining potential.  %BJC: I can reference an equilibration script that can be released with the supplemental info or something
-    \item The resulting unrestrained structure is allowed to equilibrate in the NPT
-    ensemble for 400 - 500 ns.
-  \end{itemize}
-
-  %BJC: the following paragraph will be replaced with something that Joe writes
-  Simulated X-ray diffraction patterns were generated based on atomic
-  coordinates for a direct experimental comparison.
-  \begin{itemize}
-    \item All atomic coordinates were simulated as gaussian spheres of electron
-    density corresponding to each atom's atomic number.
-    \item A three dimensional fourier transform (FT) of the array of electron 
-    density results in a three dimensional structure factor which represents
-    the unit cell in reciprocal space.
-    \item We perform an angular average of the structure factor about the 
-    z axis to generate a 2D cross section close to what one would see 
-    experimentally.
-    \item We matched experimental 2D WAXS patterns by iterative improvement
-    of our choice of initial structure and equilibration procedure.
-  \end{itemize}
-
-  \begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{}\label{fig:sandwiched}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{PD.png}
-		\caption{}\label{fig:pd}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{}\label{fig:tshaped}
-	\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwichedlayers.png}
-		\caption{}\label{fig:sandwichedlayers}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{offsetlayers.png}
-		\caption{}\label{fig:offsetlayers}
-	\end{subfigure}
-	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
-	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
-	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
-	configuration }\label{fig:stacking}
-  \end{figure}
-
-  Ionic conductivity was calculated using two different methods for
-  robustness.
-  \begin{itemize}
-    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
-    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
-    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
-    \item Sodium ion diffusion coefficients were found by calculating the slope
-    of the linear region of the mean square displacement curve as indicated by
-    the einstein relation \cite{einstein_investigations_1956}.]
-    \item Ion concentration was measured with respect to the entire unit cell. %BJC: I don't think this needs to be said
-    \item The second method, termed the 'Collective Diffusion' model, measures 
-    the movement of the collective variable, Q, which is defined as the amount
-    of charge transfer through the system.
-    \item The diffusion coefficient of Q, $D_Q$, can be calculated using the 
-    einstein relation.
-    \item The conductance, $\gamma$ of the system can be calculated as:
-    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
-    achieved by multiplying by channel length and dividing by the membrane
-    cross sectional area.
-    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
-  \end{itemize}
-
-  Using an equilibrated structure, a crosslinking procedure was performed
-  in order to better parallel synthetic procedures. 
-  \begin{itemize}
-    \item The purpose of crosslinking is to maintain macroscopic alignment of 
-    the crystalline domains, ensuring aligned, hexagonally packed pores.
-    \item For that reason, we are not concerned with replicating the kinetics 
-    of the reaction, but instead emphasize the consistency of the final structure
-    with experimental structural data.
-    \item The algorithm was developed based on the known reaction mechanism.
-    \item Crosslinking of this system is a free radical polymerization (FRP)
-    taking place between terminal vinyl groups present on each of the three
-    monomer tails.
-    \item FRPs require an initiator which bonds to the system, meaning new atoms
-    were introduced into the system.
-    \item For simplicity, the initiator was simulated as hydrogen and made present 
-    in the simulation by including them in all possible bonding positions as dummy atoms.
-    \item The crosslinking procedure is carried out iteratively.
-    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
-    \item The topology is updated with new bonds and dummy hydrogen atoms are 
-    changed to appropriate hydrogen types. 
-    \item Head-to-tail addition was the only propagation mode considered due to 
-    its dominance the real system.
-    \item Direction of attack was not considered because the resultant mixture 
-    is racemic.
-    %BJC: The following items belongs in results/discussion
-    \item The resulting crosslinked structure has an even distribution of
-    crosslinks between monomer tails of the same monomer, monomers stacked on
-    top of each other and monomers in other pores, including across periodic
-    boundaries.
-    \item The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
-    constant under a range of simulation conditions.
-  \end{itemize}
-
-  \section*{Results and Discussion}
-
-  \subsection*{Determination of Nanoscopic Structural Details}
-
-  In order to construct an initial configuration which gives reliable 
-  trends, we need to understand the composition of layers, how far apart
-  to stack the layers, and how to orient them with respect to each other.
-  \begin{itemize}
-  	\item To verify our choices for each parameter, we compare our calculations
-	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
-	scattering (WAXS), and ionic conductivity measurements.
-  \end{itemize}
-
-  To discern the composition of the monomer layers, we ran simulations of 
-  systems created with 4 - 8 monomers per layer.
-  \begin{itemize}
-  	\item Both the sandwiched and parallel displaced configurations were tested.
-	\item All systems remained stable for at least 50 ns.
-	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
-	Systems built with 5 monomers in each layer equilibrate to a pore spacing
-	that is most consistent with the experimental value of 4.12 nm derived from
-	SAXS measurements (Figure~\ref{fig:SAXS}).
-	\item We verified that the system stays partitioned into layers by plotting 
-	pair correlation functions calculated between aromatic rings along the length
-	of the pores (Fig~\ref{fig:zdf}).
-	\item The remainder of this discussion will focus on the analysis of systems
-	built with 5 monomers per layer. 
-  \end{itemize}
-
-  \begin{table}[H]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  		   & \multicolumn{2}{c}{Starting Configuration} \\
-  \hline
-  Monomers per layer & Sandwiched & Parallel Displaced \\
-  \midrule
-  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
-  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
-  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
-  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
-  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
-  \bottomrule
-  \end{tabular}
-  \caption{The pore spacing of the model increases as number of monomers
-  in each layer increases. The pore spacing of a system starting in the 
-  sandwiched configuration is systematically lower than that started in an 
-  offset configuration. Systems built with 5 monomers per layer in a parallel
-  displaced configuration result in a pore spacing closest to experimental
-  data}\label{table:p2p} 
-  \end{table}
-
-  \begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5layered.png}
-		\caption{}\label{fig:zdf_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5offset.png}
-		\caption{}\label{fig:zdf_offset}
-	\end{subfigure}
-	\caption{Pair distribution functions of aromatic carbons for the
-	(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, 
-	parallel displaced configurations. Spikes in the distribution mark
-	distinct layers. The magnitude of the spikes with respect to the 
-	average suggest that the 5 monomer per layer, sandwiched configuration
-	possesses a higher degree of layer partitioning.}\label{fig:zdf}
-  \end{figure}
-
-  Experimental WAXS measurements encode all structural details. 
-  \begin{itemize}
-  	\item There are five major features present in the 2D experimental 
-	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
-	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
-	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
-	attributed to pi-pi stacking between aromatic rings in the direction
-	perpendicular to the membrane plane, or z-axis. For simplicity, this 
-	reflection will be referred to as R-pi.
-	\item A weak intensity line is located at exactly half the qz value of
-	R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
-	real space periodic spacing of 7.4 \angstrom. This reflection has been 
-	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
-	along the z axis meaning if the positions of the aromatic rings can
-	be traced by a helix, then for each turn in the helix, there should be
-	two aromatic rings. For this reason it will be referred to as R-helix.
-	\item A third major reflection is marked by a low intensity ring located
-	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
-	corresponds to 4.5 \angstrom which is characteristic of the average 
-	spacing between packed alkane chains. This reflection will be called R-alkanes.
-	\item Within R-alkanes, are four spots of higher intensity which 
-	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
-	in their respective quadrants. In many liquid crystal systems this can be
-	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
-	\item The final major reflections correspond to the spacing and symmetry of 
-	the d\textsubscript{100} plane which can be related to the distance between
-	pores. The feature, which will be called R-pores, is characterized by dots 
-	along qz = 0. The spacing between dots is indicative of the hexagonal 
-	symmetry of the packed pores. It is easiest to interpret the data by 
-	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
-  \end{itemize}
-
-  \begin{figure}[ht]
-	\centering
-	\begin{subfigure}[t]{0.47\linewidth}
-		\centering
-		\raisebox{.2\textwidth}{%
-		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-		}
-		\caption{}\label{fig:WAXS}
-	\end{subfigure}
-	\begin{subfigure}[t]{0.43\linewidth}
-		\centering
-	%	\vspace{12mm}
-		\includegraphics[width=\linewidth]{SAXS.png}
-		\caption{}\label{fig:SAXS}
-	\end{subfigure}
-	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
-	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
-	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
-  \end{figure}
-
-  The initial distance between layers can influence the approach towards
-  equilibrium. 
-  \begin{itemize}
-  	\item Equilibrated systems built according to the 3.7 \angstrom 
-	layer spacing implied by R-pi are characterized by a defined, cylindrical and
-	open pore structure.
-	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
-	\item We will refer to this system as Basin A (Figure~\ref{fig:280K_pore}).
-	\item Simulations of systems built with layers stacked greater than 4 
-	\angstrom apart results in a pore structure characterized by high radial 
-	disorder, while still maintaining partitioning between hydrophobic and 
-	hydrophilic regions.
-	\item This will be called Basin B (Figure~\ref{fig:340K_pore}).
-	\item It is apparent that this LLC membrane may exist in at least two metastable states.
-	\item The distinct difference in pore structure exhibited by each phase will 
-	likely lead to different transport mechanisms.
-	\item Understanding which phase exists experimentally is necessary in order
-	to appropriately study the system.
-  \end{itemize}
-
-  We varied the relative interlayer orientation between sandwiched and 
-  parallel-displaced based on our knowledge of the stability of the two
-  pi-stacking modes.
-  \begin{itemize}
-  	\item We generated simulated X-ray diffraction patterns from the highly
-	restrained initial configurations created during equilibration
-	\item The patterns establish a difference between the two stacking 
-	modes (Figure~\ref{fig:XRDrestrained}).
-	\item In each pattern, R-alkanes is present at a distance of $\approx
-	1.5$ \angstrom \textsuperscript{-1} (4.2 \angstrom in real space).
-  	\item R-pi is also present in each pattern, although it appears to 
-	intersect R-alkanes because the spacing between aromatic rings is 
-	similar to the alkane chain packing.
-	\item The difference in aromatic ring spacing between experiment and
-	simulation is likely a result of the inability of GAFF to properly handle
-	aromatic interactions.
-	\item The sandwiched configuration shows R-spots in the expected location.
-	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
-	\item The parallel displaced configuration contains two lines of high 
-	intensity with maximum intensity occurring where they intersect the alkane
-	chain region due to constructive interference between the two features.
-	\item The lines are located where one would expect to see R-helix and, 
-	perhaps coincidentally, the intersection with R-alkanes occurs where one 
-	would expect to see R-spots.
-	%BJC: might save the following sentence for equilibrium trajectories
-	\item As the simulation is progressed, the full line begins to fade 
-	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
-	where R-helix exists.
-  \end{itemize}
-
-  \begin{figure}
-	\centering
-	\begin{subfigure}{0.475\textwidth}
-		\hspace{-1.2cm}
-		\centering
-		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
-		\caption{}\label{fig:rzplayeredrestrained}
-	\end{subfigure}
-	\begin{subfigure}{0.475\textwidth}
-		\hspace{-1.2cm}
-		\centering
-		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
-		\caption{}\label{fig:rzoffsetrestrained}
-	\end{subfigure}
-	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
-	with restraints placed on aromatic carbons shows all major features
-	present in experimental WAXS. Near solid lines at constant z are a result of 
-	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
-	restrained parallel displaced configuration may also contain all
-	major experimental WAXS features. One can argue that R-spots is not present
-	but it is difficult to distinguish because of its intersection with the solid
-	R-helix line. Longer simulations are necessary to determine which structure
-	is the best match to experiment}\label{fig:XRDrestrained}
-  \end{figure}
-
-  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  patterns produced from equilibrated MD trajectories shows the most consistency
-  with the sandwiched configuration in Basin A.
-  \begin{itemize}
-  	\item Systems were built in both the parallel displaced and sandwiched 
-	configurations with an intial layer spacing of 3.7 \angstrom.
-	\item A third system was created by stacking layers in the sandwiched 
-	configuration 5 \angstrom apart in order to guide it towards Basin B.
-	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
-	\item For ease of reference, the third system will be referred to as the disordered system. %BJC: omit and call it basin B
-	\item The three systems were equilibrated according to our procedure with
-	NPT simulations of greater than 400 ns.
-	\item Simulated diffration patterns were generated using portions of the
-	trajectory after equilibration.
-	\item Equilibration was detected when the distance between pores and the 
-	membrane thickness stopped changing.
-	\item Simulated diffraction patterns for all three structures are shown in 
-	Figure ~\ref{fig:XRDsim}. 
-	%BJC: maybe break into a separate paragraph starting here
-	\item The equilibrated parallel displaced structure exhibits R-alkanes and
-	R-pores in the expected locations. 
-	\item Due to low resolution, making out the individual spots of R-pores is
-	challenging and can be validated upon full spherical integration of the 3D 
-	structure factor. However, the same information can be extracted by measuring 
-	the pore spacing as described earlier.
-	\item R-pi is also present, intersecting R-alkanes at a lower q value than
-	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
-	opposed to 3.7 \angstrom.
-	\item R-helix and R-spots are also both missing.
-	\item The line which intersected both of these features in the restrained 
-	simulations faded upon equilibration which suggests that monomers in the 
-	parallel-displaced configuration may not give rise to the experimental WAXS 
-	pattern seen.
-	\item Simulated XRD of the sandwiched configuration contains all features 
-	except for R-helix.
-	\item Most notably, R-spots appears in the expected location, which suggests 
-	that there is something intrinsic to the sandwiched packing that gives rise 
-	to such features. 
-	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
-	R-helix, R-pi and R-spots are not present.
-  \end{itemize}
-
-  \begin{figure}[H]
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
-		\caption{}\label{fig:sandwich_rzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{offset_rzplot.png}
-		\caption{}\label{fig:offsetrzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{disorder_rzplot.png}
-		\caption{}\label{fig:disorder_rzplot.png}
-	\end{subfigure}
-	\caption{(a) All major features except R-helix are present in
-	XRD patterns resulting from an equilibrated sandwiched configuration 
-	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
-	(b) All major features execpt R-spots are present in XRD patterns 
-	resulting from an equilibrated parallel displaced configuration in Basin A.
-	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
-	are the only major features present in XRD patterns resulting from an 
-	equilibrated disordered phase}\label{fig:XRDsim}
-  \end{figure}
-
-  \begin{wrapfigure}{R}{0.4\textwidth}
-        \centering
-        \includegraphics[width=0.4\textwidth]{tilt.png}
-        \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}
-  \end{wrapfigure}
-
-  The spots that appear in the simulated XRD pattern of the sandwiched
-  conformation are a result of the way alkane tails pack together.
-  \begin{itemize}
-  	\item Previously, the spots in the diffraction pattern had been explained 
-	as the product of tilted alkane chains.
-	\item We measured the tilt angle of the alkane chains and showed that our 
-	system equilibrates to an average tilt angle close to zero degrees (Figure~\ref{fig:tilt}). 
-	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.
-	\item By removing atoms from the trajectory and simulating a diffraction 
-	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
-	\item Since the tails are mostly flat, we plotted the centroids of the 
-	tails and measured the angle between each centroid and its nearest neighbors
-	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
-	\item The distribution of these angles is consistent with the location of 
-	the spots (Figure~\ref{fig:angle_distribution}).
-	\item We reason that monomer tails stacked closely in the sandwiched conformation
-	are forced to splay apart and pack in between in each other which creates a
-	nearly hexagonal array of packed tails. 
-  \end{itemize}
-
-  \begin{figure}
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\hspace{-1cm}
-		\vspace{1cm}
-		\includegraphics[width=\textwidth,scale=2]{tails_topview.png}
-		\caption{}\label{fig:tails_topview}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{tails_rzplot.png}
-		\caption{}\label{fig:tails_rzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{centroids_box.png}
-		\caption{}\label{fig:centroids}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{angles_traj_layered.png}
-		\caption{}\label{fig:angle_distribution}
-	\end{subfigure}
-	\caption{(a) The trajectory can be stripped of all atoms except carbon
-	atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
-	still gives rise to R-spots. (c) Finding the center of mass and visualizing 
-	their coordinates reveals the hexagonal-like packing of the tails. (d) The 
-	distribution created by measuring the angle between each centroid (e.g. red 
-	in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
-	plane has distinct spikes near 30\degree, which is consistent with the location
-	of R-spots}\label{fig:tail_packing}
-  \end{figure}
-
-  Basin A and Basin B are two configurationally metastable basins.
-  \begin{itemize}
-  	\item We hesitate to classify the basins as separate phases.
-	\item We hypothesize that Basin B is present at higher temperatures.
-	\item This is evidenced by a simulation of a system in Basin A whose temperature
-	was linearly ramped from 280K to 340K over 100 ns.
+	\item We linearly ramped the temperature of a system in Basin A 
+	from 280K to 340K over 100 ns.
         \item Visually, there is a distinct change in pore structure from one
@@
         Basin B (Figure~\ref{fig:340K_pore}).
-	\item To quantify our observation, we chose three easily measurable order 
-	parameters: the distance between pores, the membrane thickness and the
-	ratio of pore radius to the uncertainty in pore radius.
-	\item The pore radius is divided by its uncertainty in order to understand
-	the degree to which monomers obstruct the pore region.
-	\item Referring back to our temperature ramped system, the slope of all 
-	order parameters change around 315K - 325K 
+        \item The slope of all order parameters changes between 315K and 325K
 	(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
         possibility of an abrupt change in system ordering.
-	\item To prove that the basins are in fact two different phases, we must 
-	observe evidence of a first order phase transition, which would be marked 
-	by a discontinuity in an order parameter as a function of temperature.
-	\item Our 100 ns temperature ramp may have been too fast causing the system
+        \item Our 100 ns temperature ramp was likely too fast and caused the system
         to suffer from hysteresis.
-	%BJC: should this go in methods?
-	\item To mitigate hysteresis, we performed a slow, stepwise temperature ramp.
+  \end{itemize}
+
+  In an attempt to mitigate hysteresis, we performed a slow, stepwise temperature ramp.
+  \begin{itemize}
         \item Starting from a sandwiched structure equilibrated at 280K, the system
@@
         until the system was equilibrated for 200 ns at 320K.
-	\item In all cases, we observed smooth changes in order parameters as temperature
-	was increased implying that we can not yet claim the existence of two phases 
-	(Figure~\ref{fig:phase_transition}).
-	\item I have this run out to about 335K right now. I have to see if there is anything
-	noteworthy to report
+	\item The same process was repeated with system equilibrated in Basin B and used
+	as a benchmark for comparison. 
+  \end{itemize}
 
@@
 
-  \begin{figure}
-	\centering
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_layered.png}
-		\caption{}\label{fig:p2p_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{thickness_layered.png}
-		\caption{}\label{fig:thickness_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{order_layered.png}
-		\caption{}\label{fig:order_layered}
-	\end{subfigure}
-	\caption{In all cases, blue lines represent the measured value of
-	the order parameter, black lines are average values calculated from
-	equilibrated Basin B systems at each temperature, green shaded regions
-	represent the standard deviation of each of the black line values, and 
-	red dashed lines show where the temperature is bumped to the next level.
-	(a) The pore spacing decreases smoothly as it approaches Basin B values.
-	(b) Membrane thickness increases steadily with temperature, however
-	it is still far from the Basin B value after 200 ns at 320K. (c) The
-	ratio of pore radius to is uncertainty rapidly decreases initially and
-	approaches the Basin B value smoothly until they finally overlap at 320K.}\label{fig:phase_transition}
-  \end{figure}
-
-  \subsection*{Ionic conductivity calculation}
-
-  The model gives reasonable estimates of ionic conductivity for both phases.
+  Basin A and Basin B are two configurationally metastable basins.
   \begin{itemize}
-  	\item Calculated values of ionic conductivity obtained using the Nernst 
-	Einstein relation and Collective Diffusion model are compared in 
-	Table~\ref{table:conductivity}.
-	\item The two methods agree with each other within error, although the 
-	uncertainty obtained using the Collective Diffusion model is much higher.
-	\item Much longer simulations are needed to lower the uncertainty.
-	\item  This is especially true of the value calculated for Basin B using
-	the collective diffusion model. % TODO: Run Basin B out longer
-	\item Basin A collective diffusion calculations were generated from a 
-	500 ns simulation.
-	\item In both cases, our calculated values would benefit from longer simulations. 
-	\item For this reason we will likely only use the Nernst Einstein relation
-	in future calculations of this type. 
-	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
-	\item Conductivity is enhanced in Basin B due to a higher sodium ion diffusivity.
-	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
-	Sodium ions have less ites to move to in Basin A.
-	\item No experimental evidence of this trend. May Xunda will find something
-	\item In both cases, our calculated values for Basin A are higher than the 
-	experimental values, as expected. 
-	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
-	\item However, the real system, although mostly aligned and straight, has a 
-	distribution of azimuthal angles, meaning that the pores have a degree of 
-	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
-	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
-	fold increase in ionic conductivity. We would expect additional gains in a 
-	perfectly aligned system.
+        \item There is litle change in disordered phase properties during the temperature ramp.
+	\item We observed smooth changes in order parameters as temperature
+        of the Basin A system was increased implying that we cannot claim the
+	existence of two phases (Figure~\ref{fig:phase_transition}).
+	\item The Basin A system does not converge to the same order parameter
+	values as Basin B, however they trend in the general direction.
+	\item Qualitatively, the pore structure of the Basin A system becomes
+	comparable to one characteristic of Basin B as temperature is raised.
+	\item To resolve the quanitative discrepancy, we would need a slower 
+	temperature ramp
+	\item Since there are no abrupt changes in any order parameter along the 
+	trajectory, we can conclude that the two basins are not separate phases
+	\item Basin A is the closest match to what is seen experimentally
+	\item Basin B is likely an intermediate between the Col\textsubscript{h} 
+	phase and isotropic phase
+	\item Basin B is present in our simulations at lower temperatures 
+	because our model lacks sufficient pi-pi iteractions necessary to 
+	stabilize the system into Basin A. 
   \end{itemize}
 
-  \begin{table}[H]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
-  \hline
-  Method & Basin A & Basin B \\
-  \midrule
-  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
-  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
-  Experiment & \num{1.33e-5} (0.10) & -- \\
-  \bottomrule
-  \end{tabular}
-  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
-  agree within error. Both methods give calculated values of ionic conductivity which
-  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
-  \end{table}
-
-  \subsection*{Implementation of the crosslinking algorithm}
-
-  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
-  Basin A.
-  \begin{itemize}  %BJC: working on the following
-  	\item Distribution of crosslinks
-	\item Pore spacing
-	\item X-ray diffraction
-	\item Ionic Conductivity
-  \end{itemize}
-  %BJC: THe following figure will be replaced with one representative of the new
-  % data I am  collecting above.
-  \begin{figure}[H]
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
-		\caption{}\label{fig:p2p_diagram}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
-		\caption{}\label{fig:no_xlink_p2p}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{xlink_p2p.png}
-		\caption{}\label{fig:xlink_p2p}
-	\end{subfigure}
-	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
-	Each numbered circle represents a pore. Distances are measured along each of the 
-	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
-	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
-	individual pores in the crosslinked system are stable relative to the uncrosslinked
-	system}\label{fig:xlink}
-  \end{figure}
+\end{document}

### 2017-08-31 Ben_Manuscripts/Paper1/basins.tex
updates to basin outline

@@
   \graphicspath{{./figures/}}
+
+  % Context: At this point in the manuscript, I have already narrowed the
+  % systems down to a disordered structure and the ordered sandwiched configuration
+  % I've named them Basin A and Basin B for simplicity. A - ordered, B - disordered
+  % I don't call them the ordered and disordered basins because I think that can 
+  % be misleading 
+  % I'm open to other naming ideas. 
   We can not immediately classify Basin A and Basin B as separate phases.
@@
 	between pores, the membrane thickness and the ratio of pore radius to
-	the uncertainty in pore radius.
+	the uncertainty in pore radius.  % BJC: these may change
         \item The pore radius is divided by its uncertainty as a way of quantifying
@@
         until the system was equilibrated for 200 ns at 320K.
-	\item The same process was repeated with system equilibrated in Basin B and used
+	\item The same process was repeated with a system equilibrated in Basin B and used
 	as a benchmark for comparison. 
@@
   \begin{itemize}
-        \item There is litle change in disordered phase properties during the temperature ramp.
+        \item There is litle change in disordered phase properties during the 
+        temperature ramp.
 	\item We observed smooth changes in order parameters as temperature
@@
 	existence of two phases (Figure~\ref{fig:phase_transition}).
-	\item The Basin A system does not converge to the same order parameter
-	values as Basin B, however they trend in the general direction.
 	\item Qualitatively, the pore structure of the Basin A system becomes
         comparable to one characteristic of Basin B as temperature is raised.
+	\item The Basin A system does not converge to the same order parameter
+	values as Basin B, however it is trending towards Basin B values.
 	\item To resolve the quanitative discrepancy, we would need a slower 
@@
 
+  \begin{figure}
+        \centering
+	% BJC: I'll get actual pictures of the system here. I'm not sure how 
+	% necessary this figure is though. It could go in the supplemental 
+	% information and I can reference the pictures in the previous figure
+	% since they show basically the same idea : Ordered vs. disordered pore
+	% Alternatively, I could show two diffraction patterns here from the 
+	% beginning and end temperature 
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+                \caption{}\label{fig:BasinA_280K_pore}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{340K_tramp_close.png}
+                \caption{}\label{fig:BasinB_340K_pore}
+        \end{subfigure}
+	\vskip\baselineskip
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{p2p_layered.png}
+                \caption{}\label{fig:p2p_step}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{thickness_layered.png}
+
+                \caption{}\label{fig:thickness_step}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{order_layered.png}
+                \caption{}\label{fig:order_step}
+        \end{subfigure}
+	\caption{(a) At 280K, the system is in a configuration reminiscent of
+	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
+	spacing of Basin A decreases with temperature approaching the value 
+	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
+	temperature but is far from the Basin B value. Longer equilibrations at 
+	each temperature are needed to allow the system to fully expand. (e) The ratio 
+	of pore radius to uncertainty for Basin A changes smoothly with temperature,
+	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
+  \end{figure}
+
 \end{document}

### 2017-09-01 Ben_Manuscripts/Paper1/Outline.tex
added new basin outline

@@
 
-  Basin A and Basin B are two configurationally metastable basins.
-  \begin{itemize}
-  	\item We hesitate to classify the basins as separate phases.
-	\item We hypothesize that Basin B is present at higher temperatures.
-	\item This is evidenced by a simulation of a system in Basin A whose temperature
-	was linearly ramped from 280K to 340K over 100 ns.
+  \documentclass{article}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+\usepackage{subcaption}
+\usepackage[margin=1in]{geometry}
+\usepackage{amsmath} % or simply amstext
+\usepackage{siunitx}
+\usepackage{booktabs}
+\usepackage[export]{adjustbox}
+\newcommand{\angstrom}{\textup{\AA}}
+\usepackage{cleveref}
+\usepackage{booktabs}
+\usepackage{gensymb}
+\usepackage{float}
+
+\begin{document}
+  \graphicspath{{./figures/}}
+
+  % Context: At this point in the manuscript, I have already narrowed the
+  % systems down to a disordered structure and the ordered sandwiched configuration
+  % I've named them Basin A and Basin B for simplicity. A - ordered, B - disordered
+  % I don't call them the ordered and disordered basins because I think that can 
+  % be misleading 
+  % I'm open to other naming ideas. 
+  We can not immediately classify Basin A and Basin B as separate phases.
+  \begin{itemize}
+	\item To prove the existence of two phases we need evidence of a
+	a first order phase transition.
+	\item A first order phase transition can be denoted by a discontinuity
+        of some order parameter in response to an external condition such as
+	temperature.
+	\item We chose three easily measurable order parameters: the distance
+	between pores, the membrane thickness and the ratio of pore radius to
+	the uncertainty in pore radius.  % BJC: these may change
+        \item The pore radius is divided by its uncertainty as a way of quantifying
+        the degree to which monomers obstruct the pore region.
+  \end{itemize}
+
+  Basin B is the dominant configuration at higher temperatures.
+  \begin{itemize}
+	\item We linearly ramped the temperature of a system in Basin A 
+	from 280K to 340K over 100 ns.
         \item Visually, there is a distinct change in pore structure from one
@@
         until the system was equilibrated for 200 ns at 320K.
-	\item In all cases, we observed smooth changes in order parameters as temperature
-	was increased implying that we can not yet claim the existence of two phases 
-	(Figure~\ref{fig:phase_transition}).
-	\item I have this run out to about 335K right now. I have to see if there is anything
-	noteworthy to report	
+	\item The same process was repeated with a system equilibrated in Basin B and used
+	as a benchmark for comparison. 
   \end{itemize}
@@
 
+  Basin A and Basin B are two configurationally metastable basins.
+  \begin{itemize}
+        \item There is litle change in disordered phase properties during the 
+        temperature ramp.
+	\item We observed smooth changes in order parameters as temperature
+        of the Basin A system was increased implying that we cannot claim the
+	existence of two phases (Figure~\ref{fig:phase_transition}).
+	\item Qualitatively, the pore structure of the Basin A system becomes
+        comparable to one characteristic of Basin B as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinA_340K_pore})
+	\item The Basin A system does not converge to the same order parameter
+	values as Basin B, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
+	\item To resolve the quanitative discrepancy, we would need a slower 
+	temperature ramp
+	\item Since there are no abrupt changes in any order parameter along the 
+	trajectory, we can conclude that the two basins are not separate phases
+	\item Basin A is the closest match to what is seen experimentally
+	\item Basin B is likely an intermediate between the Col\textsubscript{h} 
+	phase and isotropic phase
+	\item Basin B is present in our simulations at lower temperatures 
+	because our model lacks sufficient pi-pi iteractions necessary to 
+	stabilize the system into Basin A. 
+  \end{itemize}
+
   \begin{figure}
         \centering
-	\begin{subfigure}{0.325\textwidth}
+	% BJC: I'll get actual pictures of the system here. I'm not sure how 
+	% necessary this figure is though. It could go in the supplemental 
+	% information and I can reference the pictures in the previous figure
+	% since they show basically the same idea : Ordered vs. disordered pore
+	% Alternatively, I could show two diffraction patterns here from the 
+	% beginning and end temperature 
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+                \caption{}\label{fig:BasinA_280K_pore}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{340K_tramp_close.png}
+                \caption{}\label{fig:BasinB_340K_pore}
+        \end{subfigure}
+	\vskip\baselineskip
+        \begin{subfigure}[b]{0.325\textwidth}
                 \centering
                 \includegraphics[width=\textwidth]{p2p_layered.png}
-		\caption{}\label{fig:p2p_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.325\textwidth}
+                \caption{}\label{fig:p2p_step}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
                 \centering
                 \includegraphics[width=\textwidth]{thickness_layered.png}
-		\caption{}\label{fig:thickness_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.325\textwidth}
+
+                \caption{}\label{fig:thickness_step}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.325\textwidth}
                 \centering
                 \includegraphics[width=\textwidth]{order_layered.png}
-		\caption{}\label{fig:order_layered}
+                \caption{}\label{fig:order_step}
         \end{subfigure}
@@
 	red dashed lines show where the temperature is bumped to the next level.
-	(a) The pore spacing decreases smoothly as it approaches Basin B values.
-	(b) Membrane thickness increases steadily with temperature, however
-	it is still far from the Basin B value after 200 ns at 320K. (c) The
-	ratio of pore radius to is uncertainty rapidly decreases initially and
-	approaches the Basin B value smoothly until they finally overlap at 320K.}\label{fig:phase_transition}
+	(a) At 280K, the system is in a configuration reminiscent of
+	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
+	spacing of Basin A decreases with temperature approaching the value 
+	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
+	temperature but is far from the Basin B value. Longer equilibrations at 
+	each temperature are needed to allow the system to fully expand. (e) The ratio 
+	of pore radius to uncertainty for Basin A changes smoothly with temperature,
+	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
   \end{figure}

### 2017-09-03 Ben_Manuscripts/Paper1/Outline.tex
Updated outline test.
Lots of comments.

@@
 \usepackage{float}
-\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
+%MRS: paper needs a conclusions section outlined.
+%MRS: maybe replace pi with $\pi$,qz with $q_z$, and \angstrom by \angstrom~ (the tilde is an enforced space)
+%MRS: also maybe \AA instead of \angstrom?  I can't remember which formats better in text.
+%\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
+%MRS: focus isn't really on transport, but on what the strucures are.
+\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
+%MRS: I don't know that we need to put MD simulations alone in the title, since we also do a fair amount of comparison to experiment. 
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
@@
   questions.
+%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
   \begin{itemize}
@@
     equivalent experimental structural data.
+%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems.
+That is the main rationale, and it should be made clear fairly early in the introduction.
+Very important to make your story absolutely as clear as possible.
     \item Despite having structural data, there is still information which 
@@
     disks or layers stacked on top of one another, each containing a set 
-    number of monomers. A simple simulation study of a similar molecule suggests
+    number of monomers. A simple simulation study of a similar molecule 
+%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.
+I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context.
+We thought they did something reasonable, but they really didn't.
+%suggests
+suggested
     that there are 4 monomers in each disk~\cite{zhu_methacrylated_2006}. A 
@@
     A molecular model has the best chance of directly answering this question.
-    \item Once we know the number of monomers in each layer, we still do not know how 
+%MRS: phrasing
+    %\item Once we know the number of monomers in each layer, we still do not know how 
+    Even if we knew the number of monomers in each layer, we still would not know how 
     monomers in each layer are positioned with respect to other layers. 
@@
     \item Moieties inside the pores may interact with neutral solutes, rejecting
-    on the basis of shape and size, rather than just hydrodynamic radius.
+    on the basis of shape and 
+    %MRS: size pretty much is hydrodynamic radius
+    %size, 
+    interations with specific chemical groups
+rather than just hydrodynamic radius.
+    %MRS: isn't this next point just a restatement of what was said at the top?
     \item  An atomistic understanding of pore structure and its influence on transport 
@@
   \begin{itemize}
-    \item This article will illustrate the development of a predictive molecular model 
-    and the steps taken to ensure it mimics the real system within the constraints 
-    inherent to MD.
-    \item To understand how physically realistic the model is, validation by comparison
-    to experiment is necessary. We are primarily interested in reproducing the 
+    %MRS: main finding shouldn't be the model, but the things learned from the model. New suggestion below.
+    %\item This article will illustrate the development of a predictive molecular model 
+    %and the steps taken to ensure it mimics the real system within the constraints 
+    %inherent to MD.
+    \item In this study, we build a significantly more realistic atomistic model of LLC membranes than has ever previously been done, and explore what new structural information can be gained and what structure hypotheses are supported by this model.
+
+    %MRS: this is kind of understood -- rephrasing?
+    %\item To understand how physically realistic the model is, validation by comparison
+    to experiment is necessary. 
+    \item We validate the model using as much experimental information as pissible.
+    We are %primarily 
+    most interested in reproducing the 
     conclusions about structure which have been made from X-ray diffraction (XRD) 
     experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
+    %MRS: these are really supporting items to the above: put them indented.
     \item We have comparied simulated X-ray diffraction patterns to experiment in 
@@
     \item We examined the the influence of crosslinking on membrane structure.
-    \item We have created a model that can be used to probe the large design space
+
+    %\item We have created a model that can be used to probe the large design space
     available for membrane design
-    \item The analysis used in this paper can be readily extended to the H\textsubscript{II}
+    \item The structure-building approach and analysis used in this paper can be readily extended to the H\textsubscript{II}
     phase and other similar LC systems.
@@
     \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
+    %MRS: how chosen?  randomly?  Be precise.  
     \item A low energy configuration was pulled from the trajectory 
@@
     \item To bypass the slow self-assembly process, python scripts are used
-    to assemble monomers into a structure close to the expected equilibrium 
-    configuration (Figure~\ref{fig:python}).
+    to assemble monomers into a structure close 
+    %MRS:
+    %to the expected equilibrium configuration. 
+    one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
     \item A short, restrained equilibration, followed by NPT simulations 
@@
 
-  \begin{figure}[h]
+  \begin{figure}[!ht]
 	\centering
@@
     This point will be explained in more detail later.
+    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information 
   \end{itemize}
@@
   % the bolded structural parameters
-  \begin{itemize}
+  %MRS Breaking into more structure is good. Short sentences, only 3-5 sentences per paragraph.
+  %MRS: really, this the core of the 
+  \begin{itemize}
+    %MRS: initial distance between pores -- we set the initial, and let it find where it wants to be
+    %MRS: Or is this the initial data we COMPARE to? Be more specific about the use of these numbers. The use of the data needs to be clarified, since it's main effort here. 
     \item \textbf{The distance between pores} was based on experimental SAXS data for
     this system \cite{feng_thin_2016}.
+    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere. 
     \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
@@
     \item We are interested in 5 pore-to-pore distances which should all be equal in 
-    a perfect hexagonal array. Only 4 are independent  %BJC: small figure here for clarity? supplemental info?
+    a perfect hexagonal array. Only 4 are independent  
+    %BJC: small figure here for clarity? supplemental info?
+    %MRS: probably supplemental. 
    \item Each pore spacing has its own trajectory with its own average value
@@
     \item The standard deviation of average values is reported as the uncertainty in pore spacing.
+    %MRS: initial layer spacing.  
     \item The \textbf{layer spacing} is based on experimental 2D WAXS data.
-    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom apart.
+    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
     \item It has been hypothesized that the features are a result of pi-pi
@@
     spacings greater than 4 \angstrom.
+    %MRS: pore radius is a different category isn't it? Is this an input piece of data?
+    % should be put in a different category.
     \item We estimate the \textbf{pore radius} to be 0.6 nm based on past TEM images 
@@
     of the nanoscopic pore environment.
+    %MRS: point out this is one of the things that atomistic simulation can actually do very well - 
+    % provide a clear picture of a nanoscopic environment (the questions is whether it's 
+    % providing the _right_ clear picture).
     \item When constructing pores, we chose the carboxylate carbon from the monomer
@@
     respective pores.
+    %MRS: OK, this is a variable again that we need to set. 
     \item The \textbf{relative interlayer orientation} was chosen based on clues from 
@@
     \item The T-shaped configuration was ruled out based on the inconsistency of
-    its $\approx$ 5 \angstrom equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
+    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
     \item The system's preference towards the sandwiched vs. parallel displaced 
@@
     %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
+    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
+    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.
+This is what we fix, this is what we leave as a variable.
+The analysis probably belongs later.
     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
@@
   An equilibration scheme with position restraints placed on aromatic rings
-  prevents unrealistic jumps during early equilibration steps.
+  %MRS: 
+  %prevents 
+  is required to prevent
+  unrealistic jumps during early equilibration steps.
+  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
   \begin{itemize}
@@
     ensemble for 400 - 500 ns.
+   %MRS: we should release as many scripts as is feasible, can be in a github repository.
+   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
   \end{itemize}
@@
   %BJC: the following paragraph will be replaced with something that Joe writes
+  %MRS: sounds good.
   Simulated X-ray diffraction patterns were generated based on atomic
@@
     the einstein relation \cite{einstein_investigations_1956}.]
-    \item Ion concentration was measured with respect to the entire unit cell. %BJC: I don't think this needs to be said
+    %MRS: state how you decided which was the linear region.  
+    \item Ion concentration was measured with respect to the entire unit cell. 
+    %BJC: I don't think this needs to be said
+    %MRS: probably - people might think of conduction just occurring in the pore, so clarity is good. Could potentially have a figure illustrating the two ways of calculating conductance?  
     \item The second method, termed the 'Collective Diffusion' model, measures 
@@
     einstein relation.
+    %MRS: might need a bit more mathematical description of what is done here. For example explicitly stating that the D is 
+    % the diffusion coefficient of the variable D, which is the center of the charge (I think?)
     \item The conductance, $\gamma$ of the system can be calculated as:
@@
     \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
+    %MRS: still want to state it clearly.   
   \end{itemize}
@@
     %BJC: The following items belongs in results/discussion
+    %MRS: probably. 
     \item The resulting crosslinked structure has an even distribution of
@@
 	\item All systems remained stable for at least 50 ns.
+        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
+        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
+        %MRS: remind people where the uncertainty comes from.
+
 	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
@@
 	of the pores (Fig~\ref{fig:zdf}).
+        %MRS: explain how that conclusion was reached (perioic with period X, minima was Y percent lower than mean, maxima was Y percent higher).
 	\item The remainder of this discussion will focus on the analysis of systems
@@
   \end{tabular}
-  \caption{The pore spacing of the model increases as number of monomers
+  \caption{The pore spacing 
+  %MRS added
+  (given in \angstrom)
+  of the model increases as number of monomers
   in each layer increases. The pore spacing of a system starting in the 
@@
   offset configuration. Systems built with 5 monomers per layer in a parallel
-  displaced configuration result in a pore spacing closest to experimental
-  data}\label{table:p2p} 
+  displaced configuration result in a pore spacing closest 
+  %MRS: clarified.
+  %to experimental data
+  to the experimental 4.12 \angstrom}\label{table:p2p} 
   \end{table}
 
-  \begin{figure}[h]
+  \begin{figure}[!ht]
 	\centering
@@
 	(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, 
-	parallel displaced configurations. Spikes in the distribution mark
+	parallel displaced configurations. 
+        %MRS: added some info.
+        Clear periodic maxima in the $z$ probability density indicate
+        % Spikes in the distribution mark
 	distinct layers. The magnitude of the spikes with respect to the 
@@
   Experimental WAXS measurements encode all remaining structural details. 
+  %MRS: also encodes the pore spacing
   %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
@@
 	reflection will be referred to as R-pi.
+        %MRS: why R in R-pi? for reflection?
 	\item A weak intensity line is located at exactly half the qz value of
 	R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
+        %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
 	real space periodic spacing of 7.4 \angstrom. This reflection has been 
@@
 
-  \begin{figure}[ht]
+  \begin{figure}[!ht]
 	\centering
@@
 	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
+        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
   \end{figure}
@@
 	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
-	\item We will refer to this system as Basin A (Figure~\ref{fig:abasin}).
+        %MRS: 'basin' is not that common a term, and also only makes sense if one explicitly states what 
+        %MRS: the basin is with respect to. 
+        We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
+        %\item We will refer to this system as
+        %MRS: maybe Basin O and Basin C for open and closed?
 	\item Simulations of systems built with layers stacked greater than 4 
@@
 	hydrophilic regions.
+        %MRS: see above for clarifying ``basins''.
 	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
+        %MRS: I don't think enough information has been presented to the reader yet for this to be 'apparent'.
 	\item It is apparent that this LLC membrane may exist in at least two metastable states.
@@
 	\item Understanding which phase exists experimentally is necessary in order
-	to appropriately study the system.
-  \end{itemize}
-
-  \begin{figure}
+	to appropriately study the system.  %MRS: remind people why.
+  \end{itemize}
+
+  \begin{figure}[!ht]
         \centering
@@
   \end{figure}
+
+  %MRS: by this point, it's not clear that the directions at the
+  %beginning have clearly laid out what is being done. You want all of
+  %the logic you are going to use to be laid out by the introduction,
+  %so that only the results are left to reveal.  Fit what you are doing 
+  %in the logic pattern you lay out (which may sometimes require adjusting the logic a bit)
 
@@
 	similar to the alkane chain packing.
+        %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
 	\item The difference in aromatic ring spacing between experiment and
 	simulation is likely a result of the inability of GAFF to properly handle
-	aromatic interactions.
+	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
 	\item The sandwiched configuration shows R-spots in the expected location.
@@
 
-  \begin{figure}
+  \begin{figure}[!ht]
 	\centering
@@
 	but it is difficult to distinguish because of its intersection with the solid
-	R-helix line. Longer simulations are necessary to determine which structure
-	is the best match to experiment}\label{fig:XRDrestrained}
+	R-helix line. 
+        %MRS: Longer simulations are necessary to determine which structure
+	is the best match to experiment
+        %MRS: we probably want to avoid saying this (above) if we can.
+}\label{fig:XRDrestrained}
   \end{figure}
 
+  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.
+Something to think about.
+  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
+  %MRS: make sure the figures are comparable.
+Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
   Full comparison of experimental 2D WAXS with simulated X-ray diffraction
@@
 	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
-	\item For ease of reference, the third system will be referred to as the disordered system. %BJC: omit and call it basin B
+	\item For ease of reference, the third system will be referred to as the disordered system. 
+%BJC: omit and call it basin B
+%MRS or just be consistent from the beginning.  Or call Basins O and D          
 	\item The three systems were equilibrated according to our procedure with
@@
 	trajectory after equilibration.
+%MRS: something like ``we assume the simulation has equilibrated when the distance . . . ``        
 	\item Equilibration was detected when the distance between pores and the 
@@
         \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}
+        %MRS: probably could just report this in text, put figure in supporting.
   \end{wrapfigure}
@@
 	nearly hexagonal array of packed tails. 
-  \end{itemize}
-
-  \begin{figure}
+        %MRS: hmm.  and this doens't happen in parallel displaced? I thought it did.
+        %thought it did before. Would be good to explore the equivalent of figure 9 to this, because that comparison would make it clearer what the structural reason is for the R-spots.
+  \end{itemize}
+
+  \begin{figure}[!ht]
 	\centering
@@
   \end{figure}
-
-  \documentclass{article}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-
-\begin{document}
-  \graphicspath{{./figures/}}
-
-  % Context: At this point in the manuscript, I have already narrowed the
-  % systems down to a disordered structure and the ordered sandwiched configuration
-  % I've named them Basin A and Basin B for simplicity. A - ordered, B - disordered
-  % I don't call them the ordered and disordered basins because I think that can 
-  % be misleading 
-  % I'm open to other naming ideas. 
+  %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
+  %MRS: we had talked a lot about interconversion (or conversion one way but not other?) but 
+  %MRS: I think things have changed since then? 
   We can not immediately classify Basin A and Basin B as separate phases.
@@
 
-  \begin{figure}
+  \begin{figure}[!ht]
         \centering
@@
                 \centering
+                % these next 2 figures are REALLY big (12-18M). Likely could reduce to near 0.5-1.0 MB without loss of 
+                % necessary resolution.  A few other figures could have resolution reduced.
                 \includegraphics[width=\textwidth]{280K_tramp_close.png}
@@
 	\item Qualitatively, the pore structure of the Basin A system becomes
-        comparable to one characteristic of Basin B as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinA_340K_pore})
+        comparable to one characteristic of Basin B as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
 	\item The Basin A system does not converge to the same order parameter
@@
 	\item Basin B is present in our simulations at lower temperatures 
+        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
+        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
 	because our model lacks sufficient pi-pi iteractions necessary to 
@@
         \end{subfigure}
+        %MRS: Are (a) and (b) from the nonequilibrium short run?
+        %That's not clear. Not clear it's possible to state that it's
+        %the ``right'' disordered basin if from the end of a short heating run.
+
 	\caption{In all cases, blue lines represent the measured value of
@@
 	temperature but is far from the Basin B value. Longer equilibrations at 
-	each temperature are needed to allow the system to fully expand. (e) The ratio 
+	each temperature are needed to allow the system to fully expand. 
+        %MRS: might need to explain this ratio better?
+        (e) The ratio 
 	of pore radius to uncertainty for Basin A changes smoothly with temperature,
@@
 
+  %MRS: which model? Be specific as to which of the above structural ensembles was used.
   The model gives reasonable estimates of ionic conductivity when compared to 
@@
 	Sodium ions have less sites to move to in Basin A.
+        % total number of sites is the same in both basins, correct? -- do you mean that in basin B, there are more nearby sites?
 	\item There is currently no experimental evidence of this trend. Maybe Xund will find something
@@
 
+  %MRS: the next sections maybe should be supporting?
+  %MRS: you say ``the distance decreases by 1 A'' but is that true
+  %over all of the different structures? 
+  %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
+  %MRS: you don't otherwise discuss clearly what effect crosslinking would have. 
   \subsection*{Implementation of the crosslinking algorithm}
@@
   % data I am  collecting above.
-  \begin{figure}[h]
+  \begin{figure}[!ht]
 	\centering
@@
   \end{figure}
+
+\clearpage
+\bibliography{llc}
+
 \end{document}

### 2017-09-05 Ben_Manuscripts/Paper1/Outline.tex
Intro edited and comments addressed

@@
 
-  A clear picture of the nanoscopic LLC membrane structure, gained by building 
-  a molecular model will provide evidence to answer existing and newly proposed
-  questions.
-%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
-  \begin{itemize}
-    \item We will limit our initial studies to studying assemblies formed by Na-GA3C11
-    \item We have also chosen to focus our initial efforts on the development of 
-    a model of the Col\textsubscript{h} phase membrane.
-    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-    phase is a simpler starting point, due to the absence of water, and has
-    equivalent experimental structural data.
-%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems.
-That is the main rationale, and it should be made clear fairly early in the introduction.
-Very important to make your story absolutely as clear as possible.
-    \item Despite having structural data, there is still information which 
-    experiment cannot definitively answer
-    \item The Col\textsubscript{h} phase is described as having pores made of
-    disks or layers stacked on top of one another, each containing a set 
-    number of monomers. A simple simulation study of a similar molecule 
-%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.
-I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context.
-We thought they did something reasonable, but they really didn't.
-%suggests
-suggested
-    that there are 4 monomers in each disk~\cite{zhu_methacrylated_2006}. A 
-    separate calculation based on the volume of the liquid crystal monomers proposes
-    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-    A molecular model has the best chance of directly answering this question.
-%MRS: phrasing
-    %\item Once we know the number of monomers in each layer, we still do not know how 
-    Even if we knew the number of monomers in each layer, we still would not know how 
-    monomers in each layer are positioned with respect to other layers. 
-    \item A driving force of self assembly in this system is thought to be pi-pi
-    stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
-    \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
-    advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
-    sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
-    \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
-    attraction which favors the parallel displaced configuration in all cases
-    except where the substitutions are extremely electron withdrawing
-    \cite{waller_hybrid_2006,ringer_effect_2006}.
-    \item While we might be able to provide answers to these questions using a 
-    molecular model, there remains the possibility that there is more than one 
-    metastable state associated with a given LLC system.
-    \item We must be able to identify which states can be produced experimentally
-    and what implications each state might have regarding transport properties.
-  \end{itemize}
-
-  A molecular level understanding of LLC membrane structure will provide guidelines
-  to reduce the large chemical space available to design monomers for creation of 
-  separation-specific membranes.
+  A molecular level understanding of LLC membrane structure, enabled by molecular
+  dynamics simulations, will provide guidelines to reduce the large chemical space
+  available to design monomers for creation of separation-specific membranes.
   \begin{itemize}
@@
     how to tune the chemical environment in the nanopores for effective water
-    desalination or small organic separations.
+    desalination or small organic molecule separations.
     \item Rejection studies show that this membrane can not perform separations of
@@
     %size, 
-    interations with specific chemical groups
+    interactions with specific chemical groups
 rather than just hydrodynamic radius.
     %MRS: isn't this next point just a restatement of what was said at the top?
-    \item  An atomistic understanding of pore structure and its influence on transport 
-    is necessary to identify performance bottle necks and direct design of future membranes. 
+    %BJC: yes, deleted
+  \end{itemize}
+
+  Our approach to constructing a general model will be based on the development of a
+  model of a specific LLC membrane which has ample experimental characterization. %BJC: ample too much?
+    \begin{itemize}
+    \item We have chosen to focus on assemblies formed by Na-GA3C11
+    \item We have also narrowed our scope to the development of 
+    a model of the Col\textsubscript{h} phase membrane.
+    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
+    phase is a simpler starting point, due to the absence of water, and has
+    equivalent experimental structural data.
+    \item Despite having structural data, there is still information which 
+    experiment cannot definitively answer
+    \end{itemize}
+
+%BJC: the following just seems like filler now that I've reorganized
+%   A clear picture of the nanoscopic LLC membrane structure, gained by building 
+%   a molecular model will provide evidence to answer existing and newly proposed
+%   questions.
+%     \begin{itemize}
+%     \item Despite having structural data, there is still information which 
+%     experiment cannot definitively answer
+%     \end{itemize}
+
+%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
+%BJC: I moved the logic for choice of monomer to system to model to a separate paragraph (above this).
+I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).
+
+%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems.
+That is the main rationale, and it should be made clear fairly early in the introduction.
+Very important to make your story absolutely as clear as possible.
+%BJC: I moved and edited a paragraph that was originally later on to be 2 above this one.
+I think it does a better job addressing points 2 and 3.
+And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)
+
+  We do not know the number of monomers that constitute the layers which stack
+  on top of each other to create pores.
+  \begin{itemize}
+%     \item The Col\textsubscript{h} phase is described as having pores made of
+%     disks or layers stacked on top of one another, each containing a set 
+%     number of monomers. 
+    \item A simple simulation study of a similar molecule 
+%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.
+I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context.
+We thought they did something reasonable, but they really didn't.
+%suggests
+%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
+suggested
+    that there are 4 monomers in each layer. Their estimation is based on a
+    simulated system containing only 16 total monomers which likely does not sufficiently
+    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
+    \item A separate calculation based on the volume of the liquid crystal monomers proposes
+    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
+    \item A molecular model has the best chance of directly answering this question.
+  \end{itemize}
+%MRS: phrasing
+    %\item Once we know the number of monomers in each layer, we still do not know how
+
+    Even if we knew the number of monomers in each layer, we still would not know how 
+    monomers in each layer are positioned with respect to other layers. 
+    \begin{itemize}
+      \item A driving force of self assembly in this system is thought to be pi-pi
+      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
+      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
+      advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
+      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
+      \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
+      attraction which favors the parallel displaced configuration in all cases
+      except where the substitutions are extremely electron withdrawing
+      \cite{waller_hybrid_2006,ringer_effect_2006}.
+    \end{itemize}
+
+%     \item While we might be able to provide answers to these questions using a 
+%     molecular model, there remains the possibility that there is more than one 
+%     metastable state associated with a given LLC system.
+
+% BJC: Does it make sense to talk about metastable states? It was never really a goal to figure out other metastable states. 
+  There remains the possibility that there is more than one metastable state 
+  associated with a given LLC system.
+  \begin{itemize}
+    \item We must be able to identify which states can be produced experimentally
+    and what implications each state might have regarding transport properties.
   \end{itemize}
@@
   We must show that the developed molecular model is consistent with
-  physical observations so that we can rely on conclusions drawn about % better word for trust?
+  physical observations so that we can rely on conclusions drawn about
   structural features characteristic of the system.
@@
     %inherent to MD.
-    \item In this study, we build a significantly more realistic atomistic model of LLC membranes than has ever previously been done, and explore what new structural information can be gained and what structure hypotheses are supported by this model.
+    \item In this study, we build a significantly more realistic atomistic model of LLC membranes 
+    than has ever previously been done, and explore what new structural information can be gained
+    and what structure hypotheses are supported by this model.
 
@@
     %\item To understand how physically realistic the model is, validation by comparison
-    to experiment is necessary. 
-    \item We validate the model using as much experimental information as pissible.
-    We are %primarily 
+    %to experiment is necessary. 
+    \item We validate the model using as much experimental information as possible.
+    \item We are %primarily 
     most interested in reproducing the 
@@
     experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
+    \begin{itemize}
     %MRS: these are really supporting items to the above: put them indented.
@@
 	    \item We examined the the influence of crosslinking on membrane structure.
-
+    \end{itemize}
     %\item We have created a model that can be used to probe the large design space
-    available for membrane design
-    \item The structure-building approach and analysis used in this paper can be readily extended to the H\textsubscript{II}
-    phase and other similar LC systems.
+    % available for membrane design
+    \item The structure-building approach and analysis used in this paper can be readily extended
+    to the H\textsubscript{II} phase and other similar LC systems.
   \end{itemize}

### 2017-09-05 Ben_Manuscripts/Paper1/Outline.tex
working on methods

@@
     \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
-    %MRS: how chosen?  randomly?  Be precise.  
-    \item A low energy configuration was pulled from the trajectory 
+    % MRS: how chosen? randomly? be precise
+    % BJC: added randomly to bullet point below
+    \item A low energy configuration was randomly pulled from the trajectory
     and charges were reassigned using the am1bccsym method of molcharge
@@
     %to the expected equilibrium configuration. 
-    one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
+    to one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
     \item A short, restrained equilibration, followed by NPT simulations 
@@
     %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
+    %BJC: so refer to supporting info here?
+Then put plots of diffraction data with different sized system there.
+I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense.
+And it doesn't make sense to talk about XRD this early in the methods.
   \end{itemize}
@@
   %MRS: really, this the core of the
-  \begin{itemize}
+
     %MRS: initial distance between pores -- we set the initial, and let it find where it wants to be
     %MRS: Or is this the initial data we COMPARE to? Be more specific about the use of these numbers. The use of the data needs to be clarified, since it's main effort here. 
-    \item \textbf{The distance between pores} was based on experimental SAXS data for
+  We placed monomers at an initial pore spacing, then allowed the system to settle 
+  into its preferred spacing. 
+  \begin{itemize}
+    \item Our chosen distance between pores was based on experimental SAXS data for
     this system \cite{feng_thin_2016}.
@@
     \item Statistics were generated using the bootstrapping technique.
+    %BJC: Do bootstrapping details go in supplemental?
     \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
     sampling from the original trajectory
-    % This might be too much detail. Maybe leave excess detail for 
-    \item We are interested in 5 pore-to-pore distances which should all be equal in 
-    a perfect hexagonal array. Only 4 are independent  
-    %BJC: small figure here for clarity? supplemental info?
-    %MRS: probably supplemental. 
     \item Each pore spacing has its own trajectory with its own average value
@@
     average pore spacing. 
-    \item The standard deviation of average values is reported as the uncertainty in pore spacing.
+    \item The standard deviation of average values is reported as the uncertainty in pore spacing
+    % BJC: The following will go in supplemental
+    \item We are interested in 5 pore-to-pore distances which should all be equal in 
+    a perfect hexagonal array. Only 4 are independent  
+  \end{itemize}
+
   %MRS: initial layer spacing.
-    \item The \textbf{layer spacing} is based on experimental 2D WAXS data.
+  The layer spacing is based on experimental 2D WAXS data.
+  \begin{itemize}  
     \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
@@
     spacings greater than 4 \angstrom.
+  \end{itemize}
+
     %MRS: pore radius is a different category isn't it? Is this an input piece of data?
     % should be put in a different category.
+    %BJC: Well I still have to initially place the monomers some distance away from the pore
+    % centers. That distance is informed by the experimental evidence.
+  \begin{itemize}
     \item We estimate the \textbf{pore radius} to be 0.6 nm based on past TEM images 
@@
     respective pores.
+  \end{itemize}
+
   %MRS: OK, this is a variable again that we need to set. 
+  \begin{itemize}
     \item The \textbf{relative interlayer orientation} was chosen based on clues from 

### 2017-09-05 Ben_Manuscripts/Paper1/Outline.tex
methods revised

@@
   %MRS Breaking into more structure is good. Short sentences, only 3-5 sentences per paragraph.
-  %MRS: really, this the core of the
 
@@
     %MRS: Or is this the initial data we COMPARE to? Be more specific about the use of these numbers. The use of the data needs to be clarified, since it's main effort here. 
-  We placed monomers at an initial pore spacing, then allowed the system to settle 
+  We placed pores at a chosen initial spacing, then allowed the system to settle 
   into its preferred spacing. 
@@
     %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
+    %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
     \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
@@
   %MRS: initial layer spacing.
-  The layer spacing is based on experimental 2D WAXS data.
+  We chose a layer spacing based on experimental 2D WAXS data.
   \begin{itemize}  
@@
   % centers. That distance is informed by the experimental evidence.
-  \begin{itemize}
-    \item We estimate the \textbf{pore radius} to be 0.6 nm based on past TEM images 
-    and size exclusion rejection data\cite{feng_scalable_2014,feng_thin_2016,
-    zhou_supported_2005}.
+
+  We based the pore radii of our initial configuration on past TEM and size exclusion 
+  rejection data
+  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
+  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
+  of pore radius in the initial configuration.
+  \begin{itemize}
+    \item Experimental evidence suggests uniform pores with radii of 0.6 nm a pore radius
     \item Comparing a geometric measurement of pore size derived from an 
@@
     of the nanoscopic pore environment.
+    \item Atomistic simulations do a good job of providing the level of detail we need. The challenge
+    will be to ensure that we are producing the correct picture.
     %MRS: point out this is one of the things that atomistic simulation can actually do very well - 
@@
   %MRS: OK, this is a variable again that we need to set. 
-  \begin{itemize}
-    \item The \textbf{relative interlayer orientation} was chosen based on clues from 
+  The \textbf{relative interlayer orientation} was chosen based on clues from 
   diffraction data as well as the various known stacking modes of benzene 
@@
   ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
+  \begin{itemize}
     \item The T-shaped configuration was ruled out based on the inconsistency of
@@
 The analysis probably belongs later.
-    \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
-    suggests entropic differences based on the way the tails are able to pack.
-    \item In the sandwiched configuration, all tails start out directly on top
-    of each other which may prevent closely stacked benzene rings.
-    \item In the offset configuration, the tails are placed in between each other 
-    which may allow layers to come together in a compact way.
-    \item This difference may explain, in part, which stacking mode is more favorable.
+    %BJC: Yeah, I will leave the rest for discussion
+%     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
+%     suggests entropic differences based on the way the tails are able to pack.
+%     \item In the sandwiched configuration, all tails start out directly on top
+%     of each other which may prevent closely stacked benzene rings.
+%     \item In the offset configuration, the tails are placed in between each other 
+%     which may allow layers to come together in a compact way.
+%     \item This difference may explain, in part, which stacking mode is more favorable.
   \end{itemize}
@@
   %prevents 
-  is required to prevent
-  unrealistic jumps during early equilibration steps.
+  during early equilibration steps is required to prevent high energy repulsions .
   %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
+  %BJC: 'high energy repulsions' ?
   \begin{itemize}
@@
     \item Doing so also mitigates system dependence on initial monomer configuration.
-    \item Restrained equilibrations are run in the NVT ensemble.
+    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
     \item Every 50 ps, we reduce the force constants by the square root of its 
@@
     nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
-    restraining potential.  %BJC: I can reference an equilibration script that can be released with the supplemental info or something
-    \item The resulting unrestrained structure is allowed to equilibrate in the NPT
+    restraining potential.  
+    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
     ensemble for 400 - 500 ns.
+   %BJC: I will reference an equilibration script that can be released with the supplemental info
    %MRS: we should release as many scripts as is feasible, can be in a github repository.
+   %BJC: Okay, once we submit, I will need to spend some time cleaning the scripts
    %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
+   %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
   \end{itemize}
@@
 
-  Ionic conductivity was calculated using two different methods for
-  robustness.
+  We calculated ionic conductivity using two different methods for robustness.
   \begin{itemize}
@@
     %MRS: state how you decided which was the linear region.
+    %BJC: nothing fancy other than looking at the msd plot and determing where to
+    % start fitting. I suppose I could minimize R^2 but that seems like overkill
+    \item We looked at the MSD plot to determine where to begin and end a linear fit
     \item Ion concentration was measured with respect to the entire unit cell. 
@@
     the movement of the collective variable, Q, which is defined as the amount
-    of charge transfer through the system.
-    \item The diffusion coefficient of Q, $D_Q$, can be calculated using the 
-    einstein relation.
-    %MRS: might need a bit more mathematical description of what is done here. For example explicitly stating that the D is 
-    % the diffusion coefficient of the variable D, which is the center of the charge (I think?)
+    of charge transfer through the system and can be thought to represent
+    the center of charge of the system.
     \item The conductance, $\gamma$ of the system can be calculated as:
@@
     cross sectional area.
+    \item $D_Q$ is the diffusion coefficient of the collective variable Q. It can
+    be calculated using the einstein relation.
+    %MRS: might need a bit more mathematical description of what is done here. For example explicitly stating that the D is 
+    % the diffusion coefficient of the variable Q, which is the center of the charge (I think?)
+    %BJC: yea its the center of charge since I add all of the charges together. I added something to the effect of what you are saying. Also put the equation earlier.
     \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.

### 2017-09-05 Ben_Manuscripts/Paper1/Outline.tex
editing results and discussion

@@
   	\item Both the sandwiched and parallel displaced configurations were tested.
-	\item All systems remained stable for at least 50 ns.
+	\item All systems are stable after 50 ns of simulation.  % BJC: edited this for clarity
         %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
@@
         %MRS: remind people where the uncertainty comes from.
+	%BJC: It looks like the 7 and 8 monomer systems were only run for 50 ns.
+The 4 monomer system was run for 200 ns.
+5 and 6 have a lot of data.
+7 and 8 flattened pretty quickly, so at the time I figured it wasn't worth continuing.
+But I'll extend them just to be thorough.
 
@@
         %MRS: explain how that conclusion was reached (perioic with period X, minima was Y percent lower than mean, maxima was Y percent higher).
+	%BJC: okay, need to run some calculations here.
 	\item The remainder of this discussion will focus on the analysis of systems
@@
 
-  Experimental WAXS measurements encode all remaining structural details. 
+  Experimental WAXS measurements encode all structural details. 
   %MRS: also encodes the pore spacing
+  %BJC: got rid of 'remaining' in 'remaining structural details'
   %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
@@
         %MRS: why R in R-pi? for reflection?
+	%BJC: yes, R = reflection
 	\item A weak intensity line is located at exactly half the qz value of
-	R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
+	R-pi (qz = 0.85 \angstrom$^-1$), corresponding to a 
         %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
@@
         %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
+	%BJC: 1D is from a Yale paper. I'm going to remake the figure from the raw data but will reference that
+	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
   \end{figure}

### 2017-09-06 Ben_Manuscripts/Paper1/Outline.tex
response to feedback on results and discussion

@@
   \begin{itemize}
+  	\item Our choice of distance between layers results in long-term stability of 
+	different configurations indicating that we have found more than one metastable
+	free energy basin.
   	\item Equilibrated systems built according to the 3.7 \angstrom 
@@
         %MRS: the basin is with respect to. 
-        We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
+	%BJC: added sentence to beginning of paragraph
+        \item We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
         %\item We will refer to this system as
         %MRS: maybe Basin O and Basin C for open and closed?
+	%BJC: That works but 'capital oh' might get confused with zero
 	\item Simulations of systems built with layers stacked greater than 4 
@@
         %MRS: I don't think enough information has been presented to the reader yet for this to be 'apparent'.
-	\item It is apparent that this LLC membrane may exist in at least two metastable states.
+	\item This LLC membrane may exist in at least two metastable states.
 	\item The distinct difference in pore structure exhibited by each phase will 
 	likely lead to different transport mechanisms.
-	\item Understanding which phase exists experimentally is necessary in order
-	to appropriately study the system.  %MRS: remind people why.
+	\item Because the pore structure will vary between each Basin, understanding 
+	which phase exists experimentally is necessary in order to ensure we are 
+	studying the system which actually dominates.  %MRS: remind people why.
   \end{itemize}
@@
 
-  We varied the relative interlayer orientation between sandwiched and 
+  We varied the initial relative interlayer orientation between sandwiched and 
   parallel-displaced based on our knowledge of the stability of the two
@@
   \begin{itemize}
-  	\item We generated simulated X-ray diffraction patterns from the highly
+  	\item We generated simulated X-ray diffraction patterns using simulation trajectories from the highly
 	restrained initial configurations created during equilibration
-	\item The patterns establish a difference between the two stacking 
+	\item The simulated patterns establish a difference between the two stacking 
 	modes (Figure~\ref{fig:XRDrestrained}).
@@
         %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
+	%BJC: okay added some more specific language
 	\item The difference in aromatic ring spacing between experiment and
@@
         %MRS: Longer simulations are necessary to determine which structure
-	is the best match to experiment
+	% is the best match to experiment
         %MRS: we probably want to avoid saying this (above) if we can.
@@
 	trajectory after equilibration.  
-%MRS: something like ``we assume the simulation has equilibrated when the distance . . . ``        
-	\item Equilibration was detected when the distance between pores and the 
-	membrane thickness stopped changing.
+	\item We assume the simulation has equilibrated when the distance between 
+	pores and the membrane thickness stopped changing.
 	\item Simulated diffraction patterns for all three structures are shown in 
@@
 
+% Supplemental VVV
   \begin{wrapfigure}{R}{0.4\textwidth}
@@
         %thought it did before. Would be good to explore the equivalent of figure 9 to this, because that comparison would make it clearer what the structural reason is for the R-spots.
+	%BJC: There aren't spots in parallel displaced and the distribution does not have the spikes that the sandwiched configuration does.
+At this point in the paper, I've tried to say that parallel displaced configuration is not consistent with experiment and I focus the rest of the paper on the sandwiched configuration
   \end{itemize}
@@
         %the ``right'' disordered basin if from the end of a short heating run.
+	%BJC: They are from the short run, but as I comment above, I need to 
+	% replace them with the correct figures
 
@@
 	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
-	Sodium ions have less sites to move to in Basin A.
-        % total number of sites is the same in both basins, correct? -- do you mean that in basin B, there are more nearby sites?
-	\item There is currently no experimental evidence of this trend. Maybe Xund will find something
+	Sodium ions have less nearby sites to move to in Basin A.
+	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
 	\item In both cases, our calculated values for Basin A are higher than the 
@@
 
+  \section*{Conclusion}
+
 \clearpage

### 2017-09-06 Ben_Manuscripts/Paper1/Outline.tex
Modified intro

@@
 
-% BJC: Does it make sense to talk about metastable states? It was never really a goal to figure out other metastable states. 
   There remains the possibility that there is more than one metastable state 
@@
   \begin{itemize}
-    \item We must be able to identify which states can be produced experimentally
-    and what implications each state might have regarding transport properties.
+    \item Simulating a membrane atomistically will require many atoms which further
+    limits the timescales acessible with MD
+    \item It is reasonable to expect that we will generate configurations which 
+    are kinetically trapped in a metastable free energy basin
+    \item We must be able to identify which state is produced experimentally
   \end{itemize}

### 2017-09-07 Ben_Manuscripts/Paper1/Outline.tex
added a conclusion

@@
 	perpendicular to the membrane plane, or z-axis. For simplicity, this 
-	reflection will be referred to as R-pi.
+	reflection will be referred to as R-$\pi$.
         %MRS: why R in R-pi? for reflection?
@@
 	\item A weak intensity line is located at exactly half the qz value of
-	R-pi (qz = 0.85 \angstrom$^-1$), corresponding to a 
+	R-$\pi$ (qz = 0.85 \angstrom$^-1$), corresponding to a 
         %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
@@
   	\item Equilibrated systems built according to the 3.7 \angstrom 
-	layer spacing implied by R-pi are characterized by a defined, cylindrical and
+	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
 	open pore structure.
@@
 	1.5$ \angstrom \textsuperscript{-1} (4.2 \angstrom in real space).
-  	\item R-pi is also present in each pattern, although it appears to 
+  	\item R-$\pi$ is also present in each pattern, although it appears to 
 	intersect R-alkanes because the spacing between aromatic rings is 
@@
 	the pore spacing as described earlier.
-	\item R-pi is also present, intersecting R-alkanes at a lower q value than
+	\item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
 	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
@@
 	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
-	R-helix, R-pi and R-spots are not present.
+	R-helix, R-$\pi$ and R-spots are not present.
   \end{itemize}
@@
 	XRD patterns resulting from an equilibrated sandwiched configuration 
-	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
+	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
 	(b) All major features execpt R-spots are present in XRD patterns 
@@
 
+  We have used a detailed molecular model of the Col\subscript{h} phase formed by NA-GA3C11
+  in order to study the nanoscopic structure.
+  \begin{itemize}
+  	\item While there have been efforts to model formation of various liquid crystalline 
+	phases with molecular dynamics, to our knowledge there have been no studies which 
+	attempt to examine their structure with the same level of detail presented here.
+	\item We have confirmed that monomers stay partitioned in layers.
+	\item We were able to deduce that layers are composed of 5 monomers.
+	\item We have identified two metastable basins which each consist of a set of 
+	similar monomer configurations characterized by the degree of order in the pore region.
+	\item We verified that the basins are not separate phases.
+	\item We have explored the affect of two different pi-stacking modes on the equilibrated
+	membrane strucure. 
+	\item Simulated diffration patterns generated from MD trajectories suggest that
+	the offset configuration produces a structure with the closest match to experiment. 
+	\item Even though our model only answers these questions for a system created by 
+	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
+	little extra effort. 
+  \end{itemize}
+
 \clearpage

### 2017-09-07 Ben_Manuscripts/Paper1/Outline.tex
Adding questions

@@
 
-  We do not know the number of monomers that constitute the layers which stack
-  on top of each other to create pores.
+  To further understand the nanoscopic structure of these membranes, there
+  are several key questions which we intend to answer and will be laid out 
+  and numbered in subsequent paragraphs.
+
+  (1) Do monomers partition into and persist as defined monomer layers?
+  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
+  thought to be composed of monomer layers stacked on top of each other. 
+  \begin{itemize}
+  	\item Their existence is supported by experimental evidence of strong 
+	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
+	membrane plane.
+	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
+	leaves no description of what is happening in monomer tail region
+	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
+	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
+	\item (1) Do monomers partition into and persist as defined monomer layers?
+  \end{itemize}
+
+  (2) If layers do exist, how many monomers constitute a single layer?
+  There has been definitive answer to the question in literature.
+%   We do not know the number of monomers that constitute the layers which stack
+%   on top of each other to create pores.
   \begin{itemize}
@@
 
-    Even if we knew the number of monomers in each layer, we still would not know how 
-    monomers in each layer are positioned with respect to other layers. 
+    (3) How do monomers in each layer position themselves with respect to surrounding 
+    layers?
+%     Even if we knew the number of monomers in each layer, we still would not know how 
+%     monomers in each layer are positioned with respect to other layers. 
     \begin{itemize}
@@
 
+  (4) Can the system exist in other metastable states or phases that are not
+  accessed during experiments?
   There remains the possibility that there is more than one metastable state 

### 2017-09-13 Ben_Manuscripts/Paper1/Outline.tex
Outline updates

@@
 \usepackage{float}
-%MRS: paper needs a conclusions section outlined.
-%MRS: maybe replace pi with $\pi$,qz with $q_z$, and \angstrom by \angstrom~ (the tilde is an enforced space)
-%MRS: also maybe \AA instead of \angstrom?  I can't remember which formats better in text.
-%\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
-%MRS: focus isn't really on transport, but on what the strucures are.
 \title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
-%MRS: I don't know that we need to put MD simulations alone in the title, since we also do a fair amount of comparison to experiment. 
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
@@
   (2) If layers do exist, how many monomers constitute a single layer?
-  There has been definitive answer to the question in literature.
+  There has been no definitive answer to the question in literature.
 %   We do not know the number of monomers that constitute the layers which stack
@@
     \begin{itemize}
-      \item A driving force of self assembly in this system is thought to be pi-pi
+      \item A driving force of self assembly in this system is thought to be $\pi$-$\pi$
       stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
       \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
-      advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
+      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
       sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
-      \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
+      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
       attraction which favors the parallel displaced configuration in all cases
@@
     to one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
+    %\item A short, restrained equilibration, followed by NPT simulations 
+    %between 400 and 500 ns, allows the initial configuration to relax into
+    %an equilibrium configuration.
+    %\item Our logic for choosing a starting configuration and the details
+    %of the equilibration schemes are presented below.
+   \end{itemize}
+
+  We tested a number of equilibration schemes in an effort to match experiment
+  while overcoming kinetic limitations of such a large system that can easily
+  get stuck in multiple metastable states.
+    Equilibration Scheme A:
+    \item Apply position restraints to aromatic rings in order to maintain
+    orientational order. 
     \item A short, restrained equilibration, followed by NPT simulations 
@@
     \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
-    \item It has been hypothesized that the features are a result of pi-pi
+    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
     interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
     \item Our simulations tend to equilibrate to a wider interlayer spacing of
-    $\approx$ 4.1 \angstrom, which inspired separate systems starting with layer 
-    spacings greater than 4 \angstrom.
+    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
+    spacings greater than 4 \angstrom~.
   \end{itemize}
@@
 
-  An equilibration scheme with position restraints placed on aromatic rings
-  %MRS: 
-  %prevents 
-  during early equilibration steps is required to prevent high energy repulsions .
-  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
-  %BJC: 'high energy repulsions' ?
+  We tested a number of equilibration schemes of increasing complexity in an effort
+  to match experiment while overcoming kinetic limitations of such a large system 
+  that can easily get stuck in multiple metastable states. All start from an initial
+  configuration generated with chosen structure variables. 
+  \begin{itemize}
+      \item Equilibration Scheme A:
+      \begin{itemize}
+          \item Steepest descent energy minimization
+          \item Short NPT simulation (~ 5 ns ) with berendsen barostat (tau-p = 1) at 300 K 
+          \item Switch to Parrinello-Rahman (tau-p = 10) and run NPT simulation for 400 - 500 ns
+          %\item Final structure strongly influenced by monomer configuration used to build 
+      \end{itemize}
+      \item Equilibration Scheme B:
       \begin{itemize}
@@
           \item Every 50 ps, we reduce the force constants by the square root of its
-    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
-    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
-    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
-    restraining potential.  
+          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
+          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
+          slowly released until there is no more restraining potential.
           \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-    ensemble for 400 - 500 ns.
+          ensemble for 400 - 500 ns in the same way as Scheme A.
+      \end{itemize}
+      \item Equilibration Scheme C:
+      \begin{itemize} 
+          \item A system equilibrated according to scheme B is cut in half so we can access
+          longer simulation timescales
+          \item The system is simulated at 335K, close to its isotropic transition temperature, for 200 ns. % BJC: not entirely sure if it needs to be an already equilibrate structure
+          \item The structure is then linearly cooled back down to 300 K over 500 ns. 
+          \item The system size is doubled back to its original size and equilibrated for 200 ns at 300 K.
+          \item Tried with and without an applied electric field.
+      \end{itemize}
+      \item Equilibration Scheme D:
+      \begin{itemize}
+          \item Even in the near dry Col\textsubscript{h} system, there exists an
+          equilibrium concentration of water.
+          \item The hydrogen bonding network formed by the water may play a role 
+          in structuring the pore.
+          \item We obtained an estimate of equilibrium pore water content by solvating
+          an initial configuration with water baths above and below the membrane. 
+	  \item We ran the solvated system according to Scheme A but for 1000 ns
+          \item Using that number we added water to the pores of an initial 
+	  configuration and equilibrated according to scheme B. 
+      \end{itemize}
+      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1
+  \end{itemize}
+
+%  An equilibration scheme with position restraints placed on aromatic rings
+  %MRS: 
+  %prevents 
+%  during early equilibration steps is required to prevent high energy repulsions .
+  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
+  %BJC: 'high energy repulsions' ?
+%  \begin{itemize}
+%    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
+%    configurations while allowing monomer tails to settle.
+%    \item Doing so also mitigates system dependence on initial monomer configuration.
+%    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
+%    \item Every 50 ps, we reduce the force constants by the square root of its 
+%    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
+%    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
+%    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
+%    restraining potential.  
+%    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
+%    ensemble for 400 - 500 ns.
    %BJC: I will reference an equilibration script that can be released with the supplemental info
@@
    %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
-  \end{itemize}
+%  \end{itemize}
 
@@
     the unit cell in reciprocal space.
-    \item We perform an angular average of the structure factor about the 
+   % \item We perform an angular average of the structure factor about the 
     z axis to generate a 2D cross section close to what one would see 
@@
 	\end{subfigure}
-	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
-	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
+	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
+	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
 	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
@@
     boundaries.
-    \item The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
+    \item The pore spacing shrinks by $\approx$ 1 \angstrom~ and stays 
     constant under a range of simulation conditions.
@@
   %MRS added
-  (given in \angstrom)
+  (given in \angstrom~)
   of the model increases as number of monomers
@@
   %to experimental data
-  to the experimental 4.12 \angstrom}\label{table:p2p} 
+  to the experimental 4.12 \angstrom~}\label{table:p2p} 
   \end{table}
@@
 	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
-	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
-	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
-	attributed to pi-pi stacking between aromatic rings in the direction
+	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
+	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
+	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
 	perpendicular to the membrane plane, or z-axis. For simplicity, this 
@@
 	%BJC: yes, R = reflection
-	\item A weak intensity line is located at exactly half the qz value of
-	R-$\pi$ (qz = 0.85 \angstrom$^-1$), corresponding to a 
-        %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
-	real space periodic spacing of 7.4 \angstrom. This reflection has been 
+	\item A weak intensity line is located at exactly half the $q_z$ value of
+	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
+	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
 	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
@@
 	\item A third major reflection is marked by a low intensity ring located
-	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
-	corresponds to 4.5 \angstrom which is characteristic of the average 
+	at r = 1.4 \angstrom$^-1$. The real space separation 
+	corresponds to 4.5 \angstrom~ which is characteristic of the average 
 	spacing between packed alkane chains. This reflection will be called R-alkanes.
 	\item Within R-alkanes, are four spots of higher intensity which 
-	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
+	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
 	in their respective quadrants. In many liquid crystal systems this can be
@@
 	pores. The feature, which will be called R-pores, is characterized by dots 
-	along qz = 0. The spacing between dots is indicative of the hexagonal 
+	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
 	symmetry of the packed pores. It is easiest to interpret the data by 
@@
 	free energy basin.
-  	\item Equilibrated systems built according to the 3.7 \angstrom 
+  	\item Equilibrated systems built according to the 3.7 \angstrom~ 
 	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
@@
 	\item Simulations of systems built with layers stacked greater than 4 
-	\angstrom apart results in a pore structure characterized by high radial 
+	\angstrom~ apart results in a pore structure characterized by high radial 
 	disorder, while still maintaining partitioning between hydrophobic and 
@@
 	\item In each pattern, R-alkanes is present at a distance of $\approx
-	1.5$ \angstrom \textsuperscript{-1} (4.2 \angstrom in real space).
+	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
   	\item R-$\pi$ is also present in each pattern, although it appears to 
@@
   	\item Systems were built in both the parallel displaced and sandwiched 
-	configurations with an intial layer spacing of 3.7 \angstrom.
+	configurations with an intial layer spacing of 3.7 \angstrom~.
 	\item A third system was created by stacking layers in the sandwiched 
-	configuration 5 \angstrom apart in order to guide it towards Basin B.
+	configuration 5 \angstrom~apart in order to guide it towards Basin B.
 	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
@@
 	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
-	opposed to 3.7 \angstrom.
+	opposed to 3.7 \angstrom~.
 	\item R-helix and R-spots are also both missing.
@@
         %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
-	because our model lacks sufficient pi-pi iteractions necessary to 
+	because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
 	stabilize the system into Basin A. 
@@
 	including periodic boundaries.
-	\item The distance between pores shrinks by 1 \angstrom after the system is 
+	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
 	crosslinked
@@
 	\item We verified that the basins are not separate phases.
-	\item We have explored the affect of two different pi-stacking modes on the equilibrated
+	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
 	membrane strucure. 

### 2017-09-13 llclib/file_rw.py

@@ -13,7 +13,7 @@ from past.utils import old_div
 import numpy as np
 import copy
 import math
-from Scripts import Periodic_Images
+import Periodic_Images
 from . import transform
 import mdtraj as md
 import os

### 2017-09-20 Ben_Manuscripts/Paper1/Outline.tex
working on paper

@@
   %MRS: sounds good.
+
+  % The following methodology is taken from the 2014 Feng et al. paper where
+  % WAXS is reported. The data we are using comes from the 2016 paper which 
+  % I assume used the same set up but I will need to verify this with Xunda
+  % before this gets sent out. The SAXS is the same as shown in the 2016 paper
+  % however I will likely reproduce it with matplotlib 
+  Experimental wide angle X-ray scattering measurements were performed using a 
+  Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
+  ($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
+  calibrations of the resultant 2-D WAXS patterns were done by using a 
+  silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
+  patterns were integrated into 1-D plots of scattering intensity (I) versus
+  q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
+  2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.
+
   Simulated X-ray diffraction patterns were generated based on atomic
@@
 
-  In order to construct an initial configuration which gives reliable 
-  trends, we need to understand the composition of layers, how far apart
-  to stack the layers, and how to orient them with respect to each other.
-  \begin{itemize}
-  	\item To verify our choices for each parameter, we compare our calculations
-	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
-	scattering (WAXS), and ionic conductivity measurements.
-  \end{itemize}
-
-  To discern the composition of the monomer layers, we ran simulations of 
-  systems created with 4 - 8 monomers per layer.
+  %In order to construct an initial configuration which gives reliable 
+  %trends, we need to understand the composition of layers, how far apart
+  %to stack the layers, and how to orient them with respect to each other.
+  %\begin{itemize}
+  %	\item To verify our choices for each parameter, we compare our calculations
+  %	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
+  %	scattering (WAXS), and ionic conductivity measurements.
+  %\end{itemize}
+
+  We will now address the questions raised in the introduction in the order
+  that they were asked.
+
+  To answer (1), we verified that the system stays partitioned into layers by
+  plotting the pair correlation function calculated between aromatic rings along
+  the length of the pores (Fig~\ref{fig:zdf}).
+  \begin{itemize}
+	\item Period of fluctuation (layer spacing)
+        \item Magnitude of fluctuations
+	\item Comment on difference between offset/layered, number of monomers per layer
+  \end{itemize}
+
+  To discern the composition of the monomer layers, addressing (2), we ran 
+  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
   \begin{itemize}
@@
 But I'll extend them just to be thorough.
-
 	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
@@
 	SAXS measurements (Figure~\ref{fig:SAXS}).
-	\item We verified that the system stays partitioned into layers by plotting 
-	pair correlation functions calculated between aromatic rings along the length
-	of the pores (Fig~\ref{fig:zdf}).
-        %MRS: explain how that conclusion was reached (perioic with period X, minima was Y percent lower than mean, maxima was Y percent higher).
-	%BJC: okay, need to run some calculations here.
 	\item The remainder of this discussion will focus on the analysis of systems
@@
 
-  Experimental WAXS measurements encode all structural details. 
+  To answer question (3) we require high resolution experimental evidence which we 
+  can match to our simulations. Experimental WAXS measurements encode all structural
+  details and we would like to match them as well as possible. 
   %MRS: also encodes the pore spacing
@@
 
-  The initial distance between layers can influence the approach towards
-  equilibrium. 
+  We were inspired to ask question (4) when we observed that the initial distance
+  between layers can influence the approach towards equilibrium. 
   \begin{itemize}
@@
 	open pore structure.
-	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
-        %MRS: 'basin' is not that common a term, and also only makes sense if one explicitly states what 
-        %MRS: the basin is with respect to. 
-	%BJC: added sentence to beginning of paragraph
-        \item We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
-        %\item We will refer to this system as
-        %MRS: maybe Basin O and Basin C for open and closed?
-	%BJC: That works but 'capital oh' might get confused with zero
+        \item We will refer to this large set of configurations, with an open pore, as 
+        Basin OP (open pore) (Figure~\ref{fig:abasin}).
 	\item Simulations of systems built with layers stacked greater than 4 
@@
 	hydrophilic regions.
-        %MRS: see above for clarifying ``basins''.
-	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
-        %MRS: I don't think enough information has been presented to the reader yet for this to be 'apparent'.
+	\item This will be called Basin CP (closed pore) (Figure~\ref{fig:bbasin}).
 	\item This LLC membrane may exist in at least two metastable states.
@@
 	which phase exists experimentally is necessary in order to ensure we are 
-	studying the system which actually dominates.  %MRS: remind people why.
+	studying the system which actually dominates.
   \end{itemize}
@@
 
-  %MRS: by this point, it's not clear that the directions at the
-  %beginning have clearly laid out what is being done. You want all of
-  %the logic you are going to use to be laid out by the introduction,
-  %so that only the results are left to reveal.  Fit what you are doing 
-  %in the logic pattern you lay out (which may sometimes require adjusting the logic a bit)
-
-  We varied the initial relative interlayer orientation between sandwiched and 
-  parallel-displaced based on our knowledge of the stability of the two
-  pi-stacking modes.
-  \begin{itemize}
-  	\item We generated simulated X-ray diffraction patterns using simulation trajectories from the highly
-	restrained initial configurations created during equilibration
-	\item The simulated patterns establish a difference between the two stacking 
-	modes (Figure~\ref{fig:XRDrestrained}).
-	\item In each pattern, R-alkanes is present at a distance of $\approx
-	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
-  	\item R-$\pi$ is also present in each pattern, although it appears to 
-	intersect R-alkanes because the spacing between aromatic rings is 
-	similar to the alkane chain packing.
-        %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
-	%BJC: okay added some more specific language
-	\item The difference in aromatic ring spacing between experiment and
-	simulation is likely a result of the inability of GAFF to properly handle
-	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
-	\item The sandwiched configuration shows R-spots in the expected location.
-	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
-	\item The parallel displaced configuration contains two lines of high 
-	intensity with maximum intensity occurring where they intersect the alkane
-	chain region due to constructive interference between the two features.
-	\item The lines are located where one would expect to see R-helix and, 
-	perhaps coincidentally, the intersection with R-alkanes occurs where one 
-	would expect to see R-spots.
+  % BJC: This paragraph needs to change since, upon inspection, it appears that the 
+  % offset configuration is correct. So it needs to shine a more positive light on offset
+  % BJC: I think it can be deleted
+  %We varied the initial relative interlayer orientation between sandwiched and 
+  %parallel-displaced based on our knowledge of the stability of the two
+  %pi-stacking modes.
+  %\begin{itemize}
+  %	\item We generated simulated X-ray diffraction patterns using simulation 
+  %      trajectories from the highly restrained initial configurations created during 
+  %	equilibration
+  %	\item The simulated patterns establish a difference between the two stacking 
+  %	modes (Figure~\ref{fig:XRDrestrained}).
+  %	\item In each pattern, R-alkanes is present at a distance of $\approx
+  %	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
+  %	\item R-$\pi$ is also present in each pattern, although it appears to 
+  %	intersect R-alkanes because the spacing between aromatic rings is 
+  %	similar to the alkane chain packing.
+  %     %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
+  %	%BJC: okay added some more specific language
+  %	\item The difference in aromatic ring spacing between experiment and
+  %	simulation is likely a result of the inability of GAFF to properly handle
+  %	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
+  %	\item The sandwiched configuration shows R-spots in the expected location.
+  %	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
+  %	\item The parallel displaced configuration contains two lines of high 
+  %	intensity with maximum intensity occurring where they intersect the alkane
+  %	chain region due to constructive interference between the two features.
+  %	\item The lines are located where one would expect to see R-helix and, 
+  %	perhaps coincidentally, the intersection with R-alkanes occurs where one 
+  %	would expect to see R-spots.
 	%BJC: might save the following sentence for equilibrium trajectories
-	\item As the simulation is progressed, the full line begins to fade 
-	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
-	where R-helix exists.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.475\textwidth}
-		\hspace{-1.2cm}
-		\centering
-		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
-		\caption{}\label{fig:rzplayeredrestrained}
-	\end{subfigure}
-	\begin{subfigure}{0.475\textwidth}
-		\hspace{-1.2cm}
-		\centering
-		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
-		\caption{}\label{fig:rzoffsetrestrained}
-	\end{subfigure}
-	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
-	with restraints placed on aromatic carbons shows all major features
-	present in experimental WAXS. Near solid lines at constant z are a result of 
-	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
-	restrained parallel displaced configuration may also contain all
-	major experimental WAXS features. One can argue that R-spots is not present
-	but it is difficult to distinguish because of its intersection with the solid
-	R-helix line. 
+  %	\item As the simulation is progressed, the full line begins to fade 
+  %	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
+  %	where R-helix exists.
+  %\end{itemize}
+
+  %\begin{figure}[!ht]
+  %	\centering
+  %	\begin{subfigure}{0.475\textwidth}
+  %		\hspace{-1.2cm}
+  %		\centering
+  %		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
+  %		\caption{}\label{fig:rzplayeredrestrained}
+  %	\end{subfigure}
+  %	\begin{subfigure}{0.475\textwidth}
+  %		\hspace{-1.2cm}
+  %		\centering
+  %		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
+  %		\caption{}\label{fig:rzoffsetrestrained}
+  %	\end{subfigure}
+  %	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
+  %	with restraints placed on aromatic carbons shows all major features
+  %	present in experimental WAXS. Near solid lines at constant z are a result of 
+  %	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
+  %	restrained parallel displaced configuration may also contain all
+  %	major experimental WAXS features. One can argue that R-spots is not present
+  %	but it is difficult to distinguish because of its intersection with the solid
+  %	R-helix line. 
         %MRS: Longer simulations are necessary to determine which structure
@@
         %MRS: we probably want to avoid saying this (above) if we can.
-}\label{fig:XRDrestrained}
-  \end{figure}
+%}\label{fig:XRDrestrained}
+%  \end{figure}
 
@@
   patterns produced from equilibrated MD trajectories shows the most consistency
-  with the sandwiched configuration in Basin A.
+  with the offset configuration in the OP basin.
   \begin{itemize}
@@
 	\item A third system was created by stacking layers in the sandwiched 
-	configuration 5 \angstrom~apart in order to guide it towards Basin B.
-	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
-	\item For ease of reference, the third system will be referred to as the disordered system. 
+	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
+	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
+	\item For ease of reference, the third system will be referred to as Basin D (disordered). 
 %BJC: omit and call it basin B
@@
         %thought it did before. Would be good to explore the equivalent of figure 9 to this, because that comparison would make it clearer what the structural reason is for the R-spots.
-	%BJC: There aren't spots in parallel displaced and the distribution does not have the spikes that the sandwiched configuration does.
-At this point in the paper, I've tried to say that parallel displaced configuration is not consistent with experiment and I focus the rest of the paper on the sandwiched configuration
   \end{itemize}

### 2017-09-21 Ben_Manuscripts/Paper1/Outline.tex
outline updates

@@
 
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
-		\caption{}\label{fig:sandwich_rzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{offset_rzplot.png}
-		\caption{}\label{fig:offsetrzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{disorder_rzplot.png}
-		\caption{}\label{fig:disorder_rzplot.png}
-	\end{subfigure}
-	\caption{(a) All major features except R-helix are present in
-	XRD patterns resulting from an equilibrated sandwiched configuration 
-	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
-	(b) All major features execpt R-spots are present in XRD patterns 
-	resulting from an equilibrated parallel displaced configuration in Basin A.
-	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
-	are the only major features present in XRD patterns resulting from an 
-	equilibrated disordered phase}\label{fig:XRDsim}
+% BJC: Replacement figure below this one
+%  \begin{figure}[!ht]
+%	\centering
+%	\begin{subfigure}{0.31\textwidth}
+%		\centering
+%		\hspace{-0.9cm}
+%		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
+%		\caption{}\label{fig:sandwich_rzplot}
+%	\end{subfigure}
+%	\begin{subfigure}{0.31\textwidth}
+%		\centering
+%		\hspace{-0.9cm}
+%		\includegraphics[width=\textwidth]{offset_rzplot.png}
+%		\caption{}\label{fig:offsetrzplot}
+%	\end{subfigure}
+%	\begin{subfigure}{0.31\textwidth}
+%		\centering
+%		\hspace{-0.9cm}
+%		\includegraphics[width=\textwidth]{disorder_rzplot.png}
+%		\caption{}\label{fig:disorder_rzplot.png}
+%	\end{subfigure}
+%	\caption{(a) All major features except R-helix are present in
+%	XRD patterns resulting from an equilibrated sandwiched configuration 
+%	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
+%	(b) All major features execpt R-spots are present in XRD patterns 
+%	resulting from an equilibrated parallel displaced configuration in Basin A.
+%	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
+%	are the only major features present in XRD patterns resulting from an 
+%	equilibrated disordered phase}\label{fig:XRDsim}
+ % \end{figure}
+
+  \begin{figure}[ht]
+  \begin{subfigure}{.83\linewidth}
+        \centering
+        \begin{subfigure}{0.4\linewidth}
+                \centering
+                \includegraphics[width=\linewidth, trim={2.5cm 0 4cm 2cm}, clip]{WAXS_raw.png}%
+                \caption{}~\label{fig:raw_waxs}
+        \end{subfigure}%
+        \begin{subfigure}{0.4\linewidth}
+                \centering
+                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_offset.png}
+                \caption{}~\label{fig:rz_offset}
+        \end{subfigure}
+        \begin{subfigure}{0.4\linewidth}
+                \centering
+                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_layered.png}
+                \caption{}~\label{fig:rz_layered}
+        \end{subfigure}%
+        \begin{subfigure}{0.4\linewidth}
+                \centering
+                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_disordered.png}
+                \caption{}~\label{fig:rz_disordered}
+        \end{subfigure}
+  \end{subfigure}%
+  \begin{subfigure}{0.14\linewidth}
+        \centering
+        \vspace{-1cm}
+        \includegraphics[width=\linewidth]{colorbar_jet.png}
+  \end{subfigure}
+  \caption{(a) Experimental 2D WAXS data contains 5 major reflections which we aim to match. The remaining
+  three images are diffraction patterns simulated from MD trajectories. (b) The parallel displaced
+  configuration gives rise to all reflections of interest. (c) The sandwiched configurations gives rise to a
+  pattern with all major reflections except R-helix. R-spots is strong relative to R-alkanes in comparison
+  to the parallel displaced configuration. (d) The disordered pore configuration creates a pattern with only
+  R-alkanes and R-pores in common with experiment}~\label{fig:xrd}
   \end{figure}
 
-% Supplemental VVV
-  \begin{wrapfigure}{R}{0.4\textwidth}
-        \centering
-        \includegraphics[width=0.4\textwidth]{tilt.png}
-        \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}
-        %MRS: probably could just report this in text, put figure in supporting.
-  \end{wrapfigure}
-
-  The spots that appear in the simulated XRD pattern of the sandwiched
-  conformation are a result of the way alkane tails pack together.
+  The spots that appear in the simulated XRD pattern of OP basin
+  conformations are a result of the way alkane tails pack together.
   \begin{itemize}
@@
 	\item We measured the tilt angle of the alkane chains and showed that our 
-	system equilibrates to an average tilt angle close to zero degrees (Figure~\ref{fig:tilt}). 
+	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
 	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.
@@
 	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
-	\item Since the tails are mostly flat, we plotted the centroids of the 
+	\item Since the tails stay nearly flat, we plotted the centroids of the 
 	tails and measured the angle between each centroid and its nearest neighbors
@@
 	nearly hexagonal array of packed tails. 
-        %MRS: hmm.  and this doens't happen in parallel displaced? I thought it did.
-        %thought it did before. Would be good to explore the equivalent of figure 9 to this, because that comparison would make it clearer what the structural reason is for the R-spots.
   \end{itemize}

### 2017-09-21 Ben_Manuscripts/Paper1/figures/xrd.tex
New images

--- 2017-09-21 Ben_Manuscripts/Paper1/Outline.tex
@@
 \usepackage{graphicx}
-\usepackage{wrapfig}
 \usepackage{subcaption}
 \usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
+
 \begin{document}
-  \bibliographystyle{ieeetr}
-  \graphicspath{{./figures/}}
-  \maketitle
-  \section*{Introduction}
-
-  Nanostructured membrane materials have become increasingly popular for 
-  aqueous separations applications such as desalination and biorefinement
-  because they offer the ability to control membrane architecture at the
-  atomic scale allowing the design of solute-specific separation membranes. \cite{humplik_nanostructured_2011}
-  \begin{itemize}
-    \item Most membrane-based aqueous separations of small molecules can 
-    be achieved using reverse osmosis (RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}
-  \end{itemize}
-
-  While RO and NF have seen many advances in the past few decades, they 
-  are far from perfect separation technologies.
-  \begin{itemize}
-    \item \textit{RO membranes}
-    \item \textbf{Inconsistent performance} : Current state-of-the-art RO membranes are unstructured with
-    tortuous and polydisperse diffusion pathways which leads to 
-    inconsistent performance \cite{song_nano_2011}
-    \item \textbf{High energy requirements} : Necessarily high feed pressures 
-    drive up energy requirements which strains developing regions and
-    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
-    \item \textbf{Separation based on differences in solubility and diffusivity}:
-    Moreover, designing RO membranes to achieve targeted separations of 
-    specific solutes is nearly impossible because various solutes dissolve
-    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
-    \item At best, one can exploit these differences to create a functional
-    selective barrier.
-    \item \textit{NF membranes}
-    \item NF was introduced as an intermediate between RO and ultrafiltration,
-    having the ability to separate organic matter and salts on the order of 
-    one nanometer in size.
-    \item Larger and well-defined pores drive down energy requirements while
-    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
-    \item NF is often used as a precursor to reverse osmosis
-    \item Unfortunately, NF membranes, like RO, are produced with a pore size 
-    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
-  \end{itemize}
-
-  Nanostructured membranes can bypass many of the performance issues which
-  plague traditional NF and RO membranes.
-  \begin{itemize}
-    \item \textbf{Tune size and functionality of building blocks} to control pore
-    size and shape: One can accomplish targeted separations with high 
-    selectivity by tuning shape, size and functionality of the molecular
-    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
-    \item As a result, solute rejecting pores can have their sizes tuned
-    uniformly, resulting in \textbf{strict size cut-offs}.
-    \item Entirely \textbf{different mechanisms} may govern transport in a given
-    nanostructured material which can inspire novel separation techniques.
-  \end{itemize}
-
-  Development of nanostructured materials has been limited by the ability
-  to synthesize and scale various fundamentally sound technologies.
-  \begin{itemize}
-    \item \textbf{Graphene sheets} are atomically thick which results in excellent
-    permeability but defects during manufacturing severely impact 
-    selectivity. \cite{cohen-tanugi_multilayer_2016}
-    \item Molecular dynamics simulations of \textbf{carbon nanotubes} show
-    promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
-    unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
-    \item \textbf{Zeolites} have sub-nm pores with a narrow pore size 
-    distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
-    however, experimental rejection was low and attributed to interstitial
-    defects formed during membrane synthesis \cite{li_desalination_2004}
-    \item There is a need for a scalable nanostructured membrane
-  \end{itemize}
-
-  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
-  aqueous separation applications. 
-  \begin{itemize}
-    \item LLCs share the characteristic ability of nanostructured membrane
-    materials to create \textbf{highly ordered structures} with the added benefits
-    of \textbf{low cost} and synthetic techniques feasible for 
-    \textbf{large scale production} \cite{feng_scalable_2014}
-    \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-    phase. The presence of small amounts of water results in the H\textsubscript{II} 
-    phase.
-    \item In both cases, monomers assemble into mesophases made of hexagonally
-    packed, uniform size, cylinders with hydrophilic groups oriented inward
-    towards the pore center and hydrophobic groups facing outward.
-    \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
-    the monomer named Na-GA3C11 has been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
-    zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
-    \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
-    aligned, resulting in a low flux membrane, slowing research in the field.
-    \item In 2014, Feng et al. showed that the mesophases could be aligned 
-    using a magnetic field with subsequent crosslinking to lock the structure
-    in place \cite{feng_scalable_2014}
-    \item In 2016, Feng et al. showed that the same result could be obtained 
-    using a technique termed soft confinement \cite{feng_thin_2016}.
-    \item Following this breakthrough, research into LLC membranes has been
-    reinvigorated
-  \end{itemize}
-
-  A molecular level understanding of LLC membrane structure, enabled by molecular
-  dynamics simulations, will provide guidelines to reduce the large chemical space
-  available to design monomers for creation of separation-specific membranes.
-  \begin{itemize}
-%     \item LLCs are versatile and controllable with a \textbf{large chemical design
-%     space} available for membrane design  %BJC: redundant
-    \item  We do not yet understand how to reduce the effective pore size or 
-    how to tune the chemical environment in the nanopores for effective water
-    desalination or small organic molecule separations.
-    \item Rejection studies show that this membrane can not perform separations of
-    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
-    \item Over the past 20 years, LLC membrane studies have been limited primarily 
-    to Na-GA3C11 with some characterization done after minor structural modifications
-    \cite{resel_structural_2000}. 
-    \item Optimization has been performed through trial and error. The only source of 
-    predictive modeling has been macroscopic models which likely do not adequately describe 
-    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
-    \item It will be challenging to efficiently narrow down the design space in 
-    a laboratory setting.
-    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
-    structure which will be crucial to understanding the role of monomer structure in 
-    membrane design.
-    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
-    \item Choice of counterion may influence the establishment of a Donnan potential 
-    affecting the degree to which the membrane can exclude charged species.
-    \item Moieties inside the pores may interact with neutral solutes, rejecting
-    on the basis of shape and 
-    %MRS: size pretty much is hydrodynamic radius
-    %size, 
-    interactions with specific chemical groups
-rather than just hydrodynamic radius.
-    %MRS: isn't this next point just a restatement of what was said at the top?
-    %BJC: yes, deleted
-  \end{itemize}
-
-  Our approach to constructing a general model will be based on the development of a
-  model of a specific LLC membrane which has ample experimental characterization. %BJC: ample too much?
-    \begin{itemize}
-	    \item We have chosen to focus on assemblies formed by Na-GA3C11
-	    \item We have also narrowed our scope to the development of 
-	    a model of the Col\textsubscript{h} phase membrane.
-	    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-	    phase is a simpler starting point, due to the absence of water, and has
-	    equivalent experimental structural data.
-	    \item Despite having structural data, there is still information which 
-	    experiment cannot definitively answer
-    \end{itemize}
-
-%BJC: the following just seems like filler now that I've reorganized
-%   A clear picture of the nanoscopic LLC membrane structure, gained by building 
-%   a molecular model will provide evidence to answer existing and newly proposed
-%   questions.
-%     \begin{itemize}
-%     \item Despite having structural data, there is still information which 
-%     experiment cannot definitively answer
-%     \end{itemize}
-
-%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
-%BJC: I moved the logic for choice of monomer to system to model to a separate paragraph (above this).
-I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).
-
-%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems.
-That is the main rationale, and it should be made clear fairly early in the introduction.
-Very important to make your story absolutely as clear as possible.
-%BJC: I moved and edited a paragraph that was originally later on to be 2 above this one.
-I think it does a better job addressing points 2 and 3.
-And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)
-
-  To further understand the nanoscopic structure of these membranes, there
-  are several key questions which we intend to answer and will be laid out 
-  and numbered in subsequent paragraphs.
-
-  (1) Do monomers partition into and persist as defined monomer layers?
-  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
-  thought to be composed of monomer layers stacked on top of each other. 
-  \begin{itemize}
-  	\item Their existence is supported by experimental evidence of strong 
-	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
-	membrane plane.
-	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
-	leaves no description of what is happening in monomer tail region
-	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
-	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
-	\item (1) Do monomers partition into and persist as defined monomer layers?
-  \end{itemize}
-
-  (2) If layers do exist, how many monomers constitute a single layer?
-  There has been no definitive answer to the question in literature.
-%   We do not know the number of monomers that constitute the layers which stack
-%   on top of each other to create pores.
-  \begin{itemize}
-%     \item The Col\textsubscript{h} phase is described as having pores made of
-%     disks or layers stacked on top of one another, each containing a set 
-%     number of monomers. 
-    \item A simple simulation study of a similar molecule 
-%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.
-I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context.
-We thought they did something reasonable, but they really didn't.
-%suggests
-%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
-suggested
-    that there are 4 monomers in each layer. Their estimation is based on a
-    simulated system containing only 16 total monomers which likely does not sufficiently
-    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
-    \item A separate calculation based on the volume of the liquid crystal monomers proposes
-    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-    \item A molecular model has the best chance of directly answering this question.
-  \end{itemize}
-%MRS: phrasing
-    %\item Once we know the number of monomers in each layer, we still do not know how
-
-    (3) How do monomers in each layer position themselves with respect to surrounding 
-    layers?
-%     Even if we knew the number of monomers in each layer, we still would not know how 
-%     monomers in each layer are positioned with respect to other layers. 
-    \begin{itemize}
-      \item A driving force of self assembly in this system is thought to be $\pi$-$\pi$
-      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
-      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
-      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
-      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
-      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
-      attraction which favors the parallel displaced configuration in all cases
-      except where the substitutions are extremely electron withdrawing
-      \cite{waller_hybrid_2006,ringer_effect_2006}.
-    \end{itemize}
-
-%     \item While we might be able to provide answers to these questions using a 
-%     molecular model, there remains the possibility that there is more than one 
-%     metastable state associated with a given LLC system.
-
-  (4) Can the system exist in other metastable states or phases that are not
-  accessed during experiments?
-  There remains the possibility that there is more than one metastable state 
-  associated with a given LLC system.
-  \begin{itemize}
-    \item Simulating a membrane atomistically will require many atoms which further
-    limits the timescales acessible with MD
-    \item It is reasonable to expect that we will generate configurations which 
-    are kinetically trapped in a metastable free energy basin
-    \item We must be able to identify which state is produced experimentally
-  \end{itemize}
-
-  We must show that the developed molecular model is consistent with
-  physical observations so that we can rely on conclusions drawn about
-  structural features characteristic of the system.
-  \begin{itemize}
-    %MRS: main finding shouldn't be the model, but the things learned from the model. New suggestion below.
-    %\item This article will illustrate the development of a predictive molecular model 
-    %and the steps taken to ensure it mimics the real system within the constraints 
-    %inherent to MD.
-    \item In this study, we build a significantly more realistic atomistic model of LLC membranes 
-    than has ever previously been done, and explore what new structural information can be gained
-    and what structure hypotheses are supported by this model.
-
-    %MRS: this is kind of understood -- rephrasing?
-    %\item To understand how physically realistic the model is, validation by comparison
-    %to experiment is necessary. 
-    \item We validate the model using as much experimental information as possible.
-    \item We are %primarily 
-    most interested in reproducing the 
-    conclusions about structure which have been made from X-ray diffraction (XRD) 
-    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
-    \begin{itemize}
-    %MRS: these are really supporting items to the above: put them indented.
-	    \item We have comparied simulated X-ray diffraction patterns to experiment in 
-	    order to match major features present in the 2D patterns.
-	    \item We calculated ionic conductivity using two agreeing methods.
-	    \item We examined the the influence of crosslinking on membrane structure.
-    \end{itemize}
-    %\item We have created a model that can be used to probe the large design space
-    % available for membrane design
-    \item The structure-building approach and analysis used in this paper can be readily extended
-    to the H\textsubscript{II} phase and other similar LC systems.
-  \end{itemize}
-
-  \section*{Methods}
-
-  HII monomers were parameterized using the Generalized AMBER Forcefield
-  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
-  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
-  assigned using tools from Openeye Scientific Software. All molecular dynamics 
-  simulations were run using the latest version of Gromacs 2016. 
-  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-
-  An ensemble of characteristic, low-energy vacuum monomer configurations
-  were constructed by applying a simulated annealing process to a
-  parameterized monomer.
-  \begin{itemize}
-    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
-    % MRS: how chosen? randomly? be precise
-    % BJC: added randomly to bullet point below
-    \item A low energy configuration was randomly pulled from the trajectory
-    and charges were reassigned using the am1bccsym method of molcharge
-    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
-    \item Using the new charges, the monomer system was annealed again and monomer
-    configurations were pulled from the trajectory to be used for full
-    system construction (Figure~\ref{fig:python}a).
-  \end{itemize}
-
-  The timescale for self assembly of monomers into the hexagonal phase is
-  unknown and likely outside of a reasonable length for an atomistic
-  simulation, calling for a more efficient way to build the system. 
-  \begin{itemize}
-    \item Previous work has shown a coarse grain model self assemble into
-    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
-    \item We attempted atomistic self-assembly by packing monomers into a box 
-    using Packmol \cite{martinez_packmol:_2009}.
-    \item Simulations of greater than 100 ns show no indicators of progress 
-    towards an ordered system.
-    \item To bypass the slow self-assembly process, python scripts are used
-    to assemble monomers into a structure close 
-    %MRS:
-    %to the expected equilibrium configuration. 
-    to one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
-    %\item A short, restrained equilibration, followed by NPT simulations 
-    %between 400 and 500 ns, allows the initial configuration to relax into
-    %an equilibrium configuration.
-    %\item Our logic for choosing a starting configuration and the details
-    %of the equilibration schemes are presented below.
-   \end{itemize}
-
-  We tested a number of equilibration schemes in an effort to match experiment
-  while overcoming kinetic limitations of such a large system that can easily
-  get stuck in multiple metastable states.
-    Equilibration Scheme A:
-    \item Apply position restraints to aromatic rings in order to maintain
-    orientational order. 
-    \item A short, restrained equilibration, followed by NPT simulations 
-    between 400 and 500 ns, allows the initial configuration to relax into
-    an equilibrium configuration.
-    \item Our logic for choosing a starting configuration and the details 
-    of the equilibration schemes are presented below.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
-	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
-		configuration. (b) Monomers are rotated and assembled into layers with 
-		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
-		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
-  \end{figure}
-
-  A typical simulation volume contains four pores in a monoclinic unit cell,
-  the smallest unit cell that maintains hexagonal symmetry when extended 
-  periodically.
-  \begin{itemize}
-    \item Each pore is made of twenty stacked monomer layers with periodic 
-    continuity in the z direction, avoiding any edge effects and creating an 
-    infinite length pore ideal for studying transport.
-    \item A small number of layers is preferred in order to reduce computational
-    cost and to allow us to look at longer timescales.
-    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
-    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
-    This point will be explained in more detail later.
-    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
-    %BJC: so refer to supporting info here?
-Then put plots of diffraction data with different sized system there.
-I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense.
-And it doesn't make sense to talk about XRD this early in the methods.
-  \end{itemize}
-
-  We chose initial guesses for the remaining structural parameters based on 
-  experimental data and treated them as variables during model development.
-  %BJC: I could potentially break this paragraph into smaller paragraphs centered around
-  % the bolded structural parameters
-  %MRS Breaking into more structure is good. Short sentences, only 3-5 sentences per paragraph.
-
-    %MRS: initial distance between pores -- we set the initial, and let it find where it wants to be
-    %MRS: Or is this the initial data we COMPARE to? Be more specific about the use of these numbers. The use of the data needs to be clarified, since it's main effort here. 
-  We placed pores at a chosen initial spacing, then allowed the system to settle 
-  into its preferred spacing. 
-  \begin{itemize}
-    \item Our chosen distance between pores was based on experimental SAXS data for
-    this system \cite{feng_thin_2016}.
-    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
-    %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
-    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
-    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
-    resulting from a tightly packed initial configuration.
-    \item To calculate the equilibrated pore spacing, we measured the distance between pore
-    centers.
-    \item Pore centers were located by averaging the coordinates of sodium ions in their 
-    respective pores.
-    \item Statistics were generated using the bootstrapping technique.
-    %BJC: Do bootstrapping details go in supplemental?
-    \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
-    sampling from the original trajectory
-    \item Each pore spacing has its own trajectory with its own average value
-    \item The average value of each pore spacing is averaged to get the overall
-    average pore spacing. 
-    \item The standard deviation of average values is reported as the uncertainty in pore spacing
-    % BJC: The following will go in supplemental
-    \item We are interested in 5 pore-to-pore distances which should all be equal in 
-    a perfect hexagonal array. Only 4 are independent  
-  \end{itemize}
-
-  %MRS: initial layer spacing.
-  We chose a layer spacing based on experimental 2D WAXS data.
-  \begin{itemize}  
-    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
-    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
-    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
-    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
-    spacings greater than 4 \angstrom~.
-  \end{itemize}
-
-  %MRS: pore radius is a different category isn't it? Is this an input piece of data?
-  % should be put in a different category.
-  %BJC: Well I still have to initially place the monomers some distance away from the pore
-  % centers. That distance is informed by the experimental evidence.
-
-  We based the pore radii of our initial configuration on past TEM and size exclusion 
-  rejection data
-  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
-  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
-  of pore radius in the initial configuration.
-  \begin{itemize}
-    \item Experimental evidence suggests uniform pores with radii of 0.6 nm a pore radius
-    \item Comparing a geometric measurement of pore size derived from an 
-    atomistic model, to a less precise, experimentally derived pore size estimate,
-    will give ambiguous results.
-    \item What is meant by pore radius will not be clear until we have a clear picture
-    of the nanoscopic pore environment.
-    \item Atomistic simulations do a good job of providing the level of detail we need. The challenge
-    will be to ensure that we are producing the correct picture.
-    %MRS: point out this is one of the things that atomistic simulation can actually do very well - 
-    % provide a clear picture of a nanoscopic environment (the questions is whether it's 
-    % providing the _right_ clear picture).
-    \item When constructing pores, we chose the carboxylate carbon from the monomer
-    head group as a reference atom, and placed it a distance r from the pore center,
-    where r is the pore radius.  %BJC: figure making that clear
-    \item We will not make direct comparisons of pore radius between our model 
-    and experiment to avoid the ambiguity. 
-    \item However, we do define a pore radius based for our own purposes.
-    \item Pore radius was measured by calculating the distance between the center of 
-    mass of each aromatic ring and the center of mass of all aromatic rings in their 
-    respective pores.
-  \end{itemize}
-
-  %MRS: OK, this is a variable again that we need to set. 
-  The \textbf{relative interlayer orientation} was chosen based on clues from 
-  diffraction data as well as the various known stacking modes of benzene 
-  and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
-  ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
-  \begin{itemize}
-    \item The T-shaped configuration was ruled out based on the inconsistency of
-    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
-    \item The system's preference towards the sandwiched vs. parallel displaced 
-    stacking modes will be explored.
-    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
-    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
-    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.
-This is what we fix, this is what we leave as a variable.
-The analysis probably belongs later.
-    %BJC: Yeah, I will leave the rest for discussion
-%     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
-%     suggests entropic differences based on the way the tails are able to pack.
-%     \item In the sandwiched configuration, all tails start out directly on top
-%     of each other which may prevent closely stacked benzene rings.
-%     \item In the offset configuration, the tails are placed in between each other 
-%     which may allow layers to come together in a compact way.
-%     \item This difference may explain, in part, which stacking mode is more favorable.
-  \end{itemize}
-
-  We tested a number of equilibration schemes of increasing complexity in an effort
-  to match experiment while overcoming kinetic limitations of such a large system 
-  that can easily get stuck in multiple metastable states. All start from an initial
-  configuration generated with chosen structure variables. 
-  \begin{itemize}
-      \item Equilibration Scheme A:
-      \begin{itemize}
-          \item Steepest descent energy minimization
-          \item Short NPT simulation (~ 5 ns ) with berendsen barostat (tau-p = 1) at 300 K 
-          \item Switch to Parrinello-Rahman (tau-p = 10) and run NPT simulation for 400 - 500 ns
-          %\item Final structure strongly influenced by monomer configuration used to build 
-      \end{itemize}
-      \item Equilibration Scheme B:
-      \begin{itemize}
-          \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-          configurations while allowing monomer tails to settle.
-          \item Doing so also mitigates system dependence on initial monomer configuration.
-          \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
-          \item Every 50 ps, we reduce the force constants by the square root of its
-          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
-          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
-          slowly released until there is no more restraining potential.
-          \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-          ensemble for 400 - 500 ns in the same way as Scheme A.
-      \end{itemize}
-      \item Equilibration Scheme C:
-      \begin{itemize} 
-          \item A system equilibrated according to scheme B is cut in half so we can access
-          longer simulation timescales
-          \item The system is simulated at 335K, close to its isotropic transition temperature, for 200 ns. % BJC: not entirely sure if it needs to be an already equilibrate structure
-          \item The structure is then linearly cooled back down to 300 K over 500 ns. 
-          \item The system size is doubled back to its original size and equilibrated for 200 ns at 300 K.
-          \item Tried with and without an applied electric field.
-      \end{itemize}
-      \item Equilibration Scheme D:
-      \begin{itemize}
-          \item Even in the near dry Col\textsubscript{h} system, there exists an
-          equilibrium concentration of water.
-          \item The hydrogen bonding network formed by the water may play a role 
-          in structuring the pore.
-          \item We obtained an estimate of equilibrium pore water content by solvating
-          an initial configuration with water baths above and below the membrane. 
-	  \item We ran the solvated system according to Scheme A but for 1000 ns
-          \item Using that number we added water to the pores of an initial 
-	  configuration and equilibrated according to scheme B. 
-      \end{itemize}
-      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1
-  \end{itemize}
-
-%  An equilibration scheme with position restraints placed on aromatic rings
-  %MRS: 
-  %prevents 
-%  during early equilibration steps is required to prevent high energy repulsions .
-  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
-  %BJC: 'high energy repulsions' ?
-%  \begin{itemize}
-%    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-%    configurations while allowing monomer tails to settle.
-%    \item Doing so also mitigates system dependence on initial monomer configuration.
-%    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
-%    \item Every 50 ps, we reduce the force constants by the square root of its 
-%    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
-%    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
-%    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
-%    restraining potential.  
-%    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-%    ensemble for 400 - 500 ns.
-   %BJC: I will reference an equilibration script that can be released with the supplemental info
-   %MRS: we should release as many scripts as is feasible, can be in a github repository.
-   %BJC: Okay, once we submit, I will need to spend some time cleaning the scripts
-   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
-   %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
-%  \end{itemize}
-
-  %BJC: the following paragraph will be replaced with something that Joe writes
-  %MRS: sounds good.
-
-  % The following methodology is taken from the 2014 Feng et al. paper where
-  % WAXS is reported. The data we are using comes from the 2016 paper which 
-  % I assume used the same set up but I will need to verify this with Xunda
-  % before this gets sent out. The SAXS is the same as shown in the 2016 paper
-  % however I will likely reproduce it with matplotlib 
-  Experimental wide angle X-ray scattering measurements were performed using a 
-  Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
-  ($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
-  calibrations of the resultant 2-D WAXS patterns were done by using a 
-  silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
-  patterns were integrated into 1-D plots of scattering intensity (I) versus
-  q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
-  2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.
-
-  Simulated X-ray diffraction patterns were generated based on atomic
-  coordinates for a direct experimental comparison.
-  \begin{itemize}
-    \item All atomic coordinates were simulated as gaussian spheres of electron
-    density corresponding to each atom's atomic number.
-    \item A three dimensional fourier transform (FT) of the array of electron 
-    density results in a three dimensional structure factor which represents
-    the unit cell in reciprocal space.
-   % \item We perform an angular average of the structure factor about the 
-    z axis to generate a 2D cross section close to what one would see 
-    experimentally.
-    \item We matched experimental 2D WAXS patterns by iterative improvement
-    of our choice of initial structure and equilibration procedure.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{}\label{fig:sandwiched}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{PD.png}
-		\caption{}\label{fig:pd}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{}\label{fig:tshaped}
-	\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwichedlayers.png}
-		\caption{}\label{fig:sandwichedlayers}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{offsetlayers.png}
-		\caption{}\label{fig:offsetlayers}
-	\end{subfigure}
-	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
-	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
-	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
-	configuration }\label{fig:stacking}
-  \end{figure}
-
-  We calculated ionic conductivity using two different methods for robustness.
-  \begin{itemize}
-    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
-    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
-    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
-    \item Sodium ion diffusion coefficients were found by calculating the slope
-    of the linear region of the mean square displacement curve as indicated by
-    the einstein relation \cite{einstein_investigations_1956}.]
-    %MRS: state how you decided which was the linear region.
-    %BJC: nothing fancy other than looking at the msd plot and determing where to
-    % start fitting. I suppose I could minimize R^2 but that seems like overkill
-    \item We looked at the MSD plot to determine where to begin and end a linear fit
-    \item Ion concentration was measured with respect to the entire unit cell. 
-    %BJC: I don't think this needs to be said
-    %MRS: probably - people might think of conduction just occurring in the pore, so clarity is good. Could potentially have a figure illustrating the two ways of calculating conductance?  
-    \item The second method, termed the 'Collective Diffusion' model, measures 
-    the movement of the collective variable, Q, which is defined as the amount
-    of charge transfer through the system and can be thought to represent
-    the center of charge of the system.
-    \item The conductance, $\gamma$ of the system can be calculated as:
-    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
-    achieved by multiplying by channel length and dividing by the membrane
-    cross sectional area.
-    \item $D_Q$ is the diffusion coefficient of the collective variable Q. It can
-    be calculated using the einstein relation.
-    %MRS: might need a bit more mathematical description of what is done here. For example explicitly stating that the D is 
-    % the diffusion coefficient of the variable Q, which is the center of the charge (I think?)
-    %BJC: yea its the center of charge since I add all of the charges together. I added something to the effect of what you are saying. Also put the equation earlier.
-    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
-    %MRS: still want to state it clearly.   
-  \end{itemize}
-
-  Using an equilibrated structure, a crosslinking procedure was performed
-  in order to better parallel synthetic procedures. 
-  \begin{itemize}
-    \item The purpose of crosslinking is to maintain macroscopic alignment of 
-    the crystalline domains, ensuring aligned, hexagonally packed pores.
-    \item For that reason, we are not concerned with replicating the kinetics 
-    of the reaction, but instead emphasize the consistency of the final structure
-    with experimental structural data.
-    \item The algorithm was developed based on the known reaction mechanism.
-    \item Crosslinking of this system is a free radical polymerization (FRP)
-    taking place between terminal vinyl groups present on each of the three
-    monomer tails.
-    \item FRPs require an initiator which bonds to the system, meaning new atoms
-    were introduced into the system.
-    \item For simplicity, the initiator was simulated as hydrogen and made present 
-    in the simulation by including them in all possible bonding positions as dummy atoms.
-    \item The crosslinking procedure is carried out iteratively.
-    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
-    \item The topology is updated with new bonds and dummy hydrogen atoms are 
-    changed to appropriate hydrogen types. 
-    \item Head-to-tail addition was the only propagation mode considered due to 
-    its dominance the real system.
-    \item Direction of attack was not considered because the resultant mixture 
-    is racemic.
-    %BJC: The following items belongs in results/discussion
-    %MRS: probably. 
-    \item The resulting crosslinked structure has an even distribution of
-    crosslinks between monomer tails of the same monomer, monomers stacked on
-    top of each other and monomers in other pores, including across periodic
-    boundaries.
-    \item The pore spacing shrinks by $\approx$ 1 \angstrom~ and stays 
-    constant under a range of simulation conditions.
-  \end{itemize}
-
-  \section*{Results and Discussion}
-
-  \subsection*{Determination of Nanoscopic Structural Details}
-
-  %In order to construct an initial configuration which gives reliable 
-  %trends, we need to understand the composition of layers, how far apart
-  %to stack the layers, and how to orient them with respect to each other.
-  %\begin{itemize}
-  %	\item To verify our choices for each parameter, we compare our calculations
-  %	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
-  %	scattering (WAXS), and ionic conductivity measurements.
-  %\end{itemize}
-
-  We will now address the questions raised in the introduction in the order
-  that they were asked.
-
-  To answer (1), we verified that the system stays partitioned into layers by
-  plotting the pair correlation function calculated between aromatic rings along
-  the length of the pores (Fig~\ref{fig:zdf}).
-  \begin{itemize}
-	\item Period of fluctuation (layer spacing)
-        \item Magnitude of fluctuations
-	\item Comment on difference between offset/layered, number of monomers per layer
-  \end{itemize}
-
-  To discern the composition of the monomer layers, addressing (2), we ran 
-  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
-  \begin{itemize}
-  	\item Both the sandwiched and parallel displaced configurations were tested.
-	\item All systems are stable after 50 ns of simulation.  % BJC: edited this for clarity
-        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
-        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
-        %MRS: remind people where the uncertainty comes from.
-	%BJC: It looks like the 7 and 8 monomer systems were only run for 50 ns.
-The 4 monomer system was run for 200 ns.
-5 and 6 have a lot of data.
-7 and 8 flattened pretty quickly, so at the time I figured it wasn't worth continuing.
-But I'll extend them just to be thorough.
-	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
-	Systems built with 5 monomers in each layer equilibrate to a pore spacing
-	that is most consistent with the experimental value of 4.12 nm derived from
-	SAXS measurements (Figure~\ref{fig:SAXS}).
-	\item The remainder of this discussion will focus on the analysis of systems
-	built with 5 monomers per layer. 
-  \end{itemize}
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  		   & \multicolumn{2}{c}{Starting Configuration} \\
-  \hline
-  Monomers per layer & Sandwiched & Parallel Displaced \\
-  \midrule
-  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
-  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
-  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
-  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
-  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
-  \bottomrule
-  \end{tabular}
-  \caption{The pore spacing 
-  %MRS added
-  (given in \angstrom~)
-  of the model increases as number of monomers
-  in each layer increases. The pore spacing of a system starting in the 
-  sandwiched configuration is systematically lower than that started in an 
-  offset configuration. Systems built with 5 monomers per layer in a parallel
-  displaced configuration result in a pore spacing closest 
-  %MRS: clarified.
-  %to experimental data
-  to the experimental 4.12 \angstrom~}\label{table:p2p} 
-  \end{table}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5layered.png}
-		\caption{}\label{fig:zdf_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5offset.png}
-		\caption{}\label{fig:zdf_offset}
-	\end{subfigure}
-	\caption{Pair distribution functions of aromatic carbons for the
-	(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, 
-	parallel displaced configurations. 
-        %MRS: added some info.
-        Clear periodic maxima in the $z$ probability density indicate
-        % Spikes in the distribution mark
-	distinct layers. The magnitude of the spikes with respect to the 
-	average suggest that the 5 monomer per layer, sandwiched configuration
-	possesses a higher degree of layer partitioning.}\label{fig:zdf}
-  \end{figure}
-
-  To answer question (3) we require high resolution experimental evidence which we 
-  can match to our simulations. Experimental WAXS measurements encode all structural
-  details and we would like to match them as well as possible. 
-  %MRS: also encodes the pore spacing
-  %BJC: got rid of 'remaining' in 'remaining structural details'
-  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
-  \begin{itemize}
-  	\item There are five major features present in the 2D experimental 
-	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
-	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
-	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
-	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-	perpendicular to the membrane plane, or z-axis. For simplicity, this 
-	reflection will be referred to as R-$\pi$.
-        %MRS: why R in R-pi? for reflection?
-	%BJC: yes, R = reflection
-	\item A weak intensity line is located at exactly half the $q_z$ value of
-	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
-	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
-	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
-	along the z axis meaning if the positions of the aromatic rings can
-	be traced by a helix, then for each turn in the helix, there should be
-	two aromatic rings. For this reason it will be referred to as R-helix.
-	\item A third major reflection is marked by a low intensity ring located
-	at r = 1.4 \angstrom$^-1$. The real space separation 
-	corresponds to 4.5 \angstrom~ which is characteristic of the average 
-	spacing between packed alkane chains. This reflection will be called R-alkanes.
-	\item Within R-alkanes, are four spots of higher intensity which 
-	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
-	in their respective quadrants. In many liquid crystal systems this can be
-	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
-	\item The final major reflections correspond to the spacing and symmetry of 
-	the d\textsubscript{100} plane which can be related to the distance between
-	pores. The feature, which will be called R-pores, is characterized by dots 
-	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
-	symmetry of the packed pores. It is easiest to interpret the data by 
-	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}[t]{0.47\linewidth}
-		\centering
-		\raisebox{.2\textwidth}{%
-		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-		}
-		\caption{}\label{fig:WAXS}
-	\end{subfigure}
-	\begin{subfigure}[t]{0.43\linewidth}
-		\centering
-	%	\vspace{12mm}
-		\includegraphics[width=\linewidth]{SAXS.png}
-		\caption{}\label{fig:SAXS}
-	\end{subfigure}
-	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
-	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
-	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
-        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
-	%BJC: 1D is from a Yale paper. I'm going to remake the figure from the raw data but will reference that
-	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
-  \end{figure}
-
-  We were inspired to ask question (4) when we observed that the initial distance
-  between layers can influence the approach towards equilibrium. 
-  \begin{itemize}
-  	\item Our choice of distance between layers results in long-term stability of 
-	different configurations indicating that we have found more than one metastable
-	free energy basin.
-  	\item Equilibrated systems built according to the 3.7 \angstrom~ 
-	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
-	open pore structure.
-        \item We will refer to this large set of configurations, with an open pore, as 
-        Basin OP (open pore) (Figure~\ref{fig:abasin}).
-	\item Simulations of systems built with layers stacked greater than 4 
-	\angstrom~ apart results in a pore structure characterized by high radial 
-	disorder, while still maintaining partitioning between hydrophobic and 
-	hydrophilic regions.
-	\item This will be called Basin CP (closed pore) (Figure~\ref{fig:bbasin}).
-	\item This LLC membrane may exist in at least two metastable states.
-	\item The distinct difference in pore structure exhibited by each phase will 
-	likely lead to different transport mechanisms.
-	\item Because the pore structure will vary between each Basin, understanding 
-	which phase exists experimentally is necessary in order to ensure we are 
-	studying the system which actually dominates.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:abasin}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:bbasin}
-        \end{subfigure}
-	\caption{From a qualitative standpoint, Basin A (a) is characterized by a
-	hollow cylindrical pore while pores in Basin B (b) are characterized by a
-	higher degree of radial disorder}\label{fig:basins}
-  \end{figure}
-
-  % BJC: This paragraph needs to change since, upon inspection, it appears that the 
-  % offset configuration is correct. So it needs to shine a more positive light on offset
-  % BJC: I think it can be deleted
-  %We varied the initial relative interlayer orientation between sandwiched and 
-  %parallel-displaced based on our knowledge of the stability of the two
-  %pi-stacking modes.
-  %\begin{itemize}
-  %	\item We generated simulated X-ray diffraction patterns using simulation 
-  %      trajectories from the highly restrained initial configurations created during 
-  %	equilibration
-  %	\item The simulated patterns establish a difference between the two stacking 
-  %	modes (Figure~\ref{fig:XRDrestrained}).
-  %	\item In each pattern, R-alkanes is present at a distance of $\approx
-  %	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
-  %	\item R-$\pi$ is also present in each pattern, although it appears to 
-  %	intersect R-alkanes because the spacing between aromatic rings is 
-  %	similar to the alkane chain packing.
-  %     %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
-  %	%BJC: okay added some more specific language
-  %	\item The difference in aromatic ring spacing between experiment and
-  %	simulation is likely a result of the inability of GAFF to properly handle
-  %	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
-  %	\item The sandwiched configuration shows R-spots in the expected location.
-  %	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
-  %	\item The parallel displaced configuration contains two lines of high 
-  %	intensity with maximum intensity occurring where they intersect the alkane
-  %	chain region due to constructive interference between the two features.
-  %	\item The lines are located where one would expect to see R-helix and, 
-  %	perhaps coincidentally, the intersection with R-alkanes occurs where one 
-  %	would expect to see R-spots.
-	%BJC: might save the following sentence for equilibrium trajectories
-  %	\item As the simulation is progressed, the full line begins to fade 
-  %	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
-  %	where R-helix exists.
-  %\end{itemize}
-
-  %\begin{figure}[!ht]
-  %	\centering
-  %	\begin{subfigure}{0.475\textwidth}
-  %		\hspace{-1.2cm}
-  %		\centering
-  %		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
-  %		\caption{}\label{fig:rzplayeredrestrained}
-  %	\end{subfigure}
-  %	\begin{subfigure}{0.475\textwidth}
-  %		\hspace{-1.2cm}
-  %		\centering
-  %		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
-  %		\caption{}\label{fig:rzoffsetrestrained}
-  %	\end{subfigure}
-  %	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
-  %	with restraints placed on aromatic carbons shows all major features
-  %	present in experimental WAXS. Near solid lines at constant z are a result of 
-  %	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
-  %	restrained parallel displaced configuration may also contain all
-  %	major experimental WAXS features. One can argue that R-spots is not present
-  %	but it is difficult to distinguish because of its intersection with the solid
-  %	R-helix line. 
-        %MRS: Longer simulations are necessary to determine which structure
-	% is the best match to experiment
-        %MRS: we probably want to avoid saying this (above) if we can.
-%}\label{fig:XRDrestrained}
-%  \end{figure}
-
-  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.
-Something to think about.
-  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
-  %MRS: make sure the figures are comparable.
-Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
-  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  patterns produced from equilibrated MD trajectories shows the most consistency
-  with the offset configuration in the OP basin.
-  \begin{itemize}
-  	\item Systems were built in both the parallel displaced and sandwiched 
-	configurations with an intial layer spacing of 3.7 \angstrom~.
-	\item A third system was created by stacking layers in the sandwiched 
-	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
-	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
-	\item For ease of reference, the third system will be referred to as Basin D (disordered). 
-%BJC: omit and call it basin B
-%MRS or just be consistent from the beginning.  Or call Basins O and D          
-	\item The three systems were equilibrated according to our procedure with
-	NPT simulations of greater than 400 ns.
-	\item Simulated diffration patterns were generated using portions of the
-	trajectory after equilibration.  
-	\item We assume the simulation has equilibrated when the distance between 
-	pores and the membrane thickness stopped changing.
-	\item Simulated diffraction patterns for all three structures are shown in 
-	Figure ~\ref{fig:XRDsim}. 
-	%BJC: maybe break into a separate paragraph starting here
-	\item The equilibrated parallel displaced structure exhibits R-alkanes and
-	R-pores in the expected locations. 
-	\item Due to low resolution, making out the individual spots of R-pores is
-	challenging and can be validated upon full spherical integration of the 3D 
-	structure factor. However, the same information can be extracted by measuring 
-	the pore spacing as described earlier.
-	\item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
-	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
-	opposed to 3.7 \angstrom~.
-	\item R-helix and R-spots are also both missing.
-	\item The line which intersected both of these features in the restrained 
-	simulations faded upon equilibration which suggests that monomers in the 
-	parallel-displaced configuration may not give rise to the experimental WAXS 
-	pattern seen.
-	\item Simulated XRD of the sandwiched configuration contains all features 
-	except for R-helix.
-	\item Most notably, R-spots appears in the expected location, which suggests 
-	that there is something intrinsic to the sandwiched packing that gives rise 
-	to such features. 
-	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
-	R-helix, R-$\pi$ and R-spots are not present.
-  \end{itemize}
-
-% BJC: Replacement figure below this one
-%  \begin{figure}[!ht]
-%	\centering
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
-%		\caption{}\label{fig:sandwich_rzplot}
-%	\end{subfigure}
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{offset_rzplot.png}
-%		\caption{}\label{fig:offsetrzplot}
-%	\end{subfigure}
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{disorder_rzplot.png}
-%		\caption{}\label{fig:disorder_rzplot.png}
-%	\end{subfigure}
-%	\caption{(a) All major features except R-helix are present in
-%	XRD patterns resulting from an equilibrated sandwiched configuration 
-%	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
-%	(b) All major features execpt R-spots are present in XRD patterns 
-%	resulting from an equilibrated parallel displaced configuration in Basin A.
-%	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
-%	are the only major features present in XRD patterns resulting from an 
-%	equilibrated disordered phase}\label{fig:XRDsim}
- % \end{figure}
 
 \begin{figure}[ht]
+
 \begin{subfigure}{.83\linewidth}
@@
 
-  The spots that appear in the simulated XRD pattern of OP basin
-  conformations are a result of the way alkane tails pack together.
-  \begin{itemize}
-  	\item Previously, the spots in the diffraction pattern had been explained 
-	as the product of tilted alkane chains.
-	\item We measured the tilt angle of the alkane chains and showed that our 
-	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
-	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.
-	\item By removing atoms from the trajectory and simulating a diffraction 
-	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
-	\item Since the tails stay nearly flat, we plotted the centroids of the 
-	tails and measured the angle between each centroid and its nearest neighbors
-	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
-	\item The distribution of these angles is consistent with the location of 
-	the spots (Figure~\ref{fig:angle_distribution}).
-	\item We reason that monomer tails stacked closely in the sandwiched conformation
-	are forced to splay apart and pack in between in each other which creates a
-	nearly hexagonal array of packed tails. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\hspace{-1cm}
-		\vspace{1cm}
-		\includegraphics[width=\textwidth,scale=2]{tails_topview.png}
-		\caption{}\label{fig:tails_topview}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{tails_rzplot.png}
-		\caption{}\label{fig:tails_rzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{centroids_box.png}
-		\caption{}\label{fig:centroids}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{angles_traj_layered.png}
-		\caption{}\label{fig:angle_distribution}
-	\end{subfigure}
-	\caption{(a) The trajectory can be stripped of all atoms except carbon
-	atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
-	still gives rise to R-spots. (c) Finding the center of mass and visualizing 
-	their coordinates reveals the hexagonal-like packing of the tails. (d) The 
-	distribution created by measuring the angle between each centroid (e.g. red 
-	in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
-	plane has distinct spikes near 30\degree, which is consistent with the location
-	of R-spots}\label{fig:tail_packing}
-  \end{figure}
-  %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
-  %MRS: we had talked a lot about interconversion (or conversion one way but not other?) but 
-  %MRS: I think things have changed since then? 
-  We can not immediately classify Basin A and Basin B as separate phases.
-  \begin{itemize}
-	\item To prove the existence of two phases we need evidence of a
-	a first order phase transition.
-	\item A first order phase transition can be denoted by a discontinuity
-        of some order parameter in response to an external condition such as
-	temperature.
-	\item We chose three easily measurable order parameters: the distance
-	between pores, the membrane thickness and the ratio of pore radius to
-	the uncertainty in pore radius.  % BJC: these may change
-        \item The pore radius is divided by its uncertainty as a way of quantifying
-        the degree to which monomers obstruct the pore region.
-  \end{itemize}
-
-  Basin B is the dominant configuration at higher temperatures.
-  \begin{itemize}
-	\item We linearly ramped the temperature of a system in Basin A 
-	from 280K to 340K over 100 ns.
-        \item Visually, there is a distinct change in pore structure from one
-        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
-        Basin B (Figure~\ref{fig:340K_pore}).
-        \item The slope of all order parameters changes between 315K and 325K
-	(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
-        possibility of an abrupt change in system ordering.
-        \item Our 100 ns temperature ramp was likely too fast and caused the system
-        to suffer from hysteresis.
-  \end{itemize}
-
-  In an attempt to mitigate hysteresis, we performed a slow, stepwise temperature ramp.
-  \begin{itemize}
-        \item Starting from a sandwiched structure equilibrated at 280K, the system
-        temperature was raised to 300K and allowed to equilibrate for 200 ns.
-        \item At the end of 200 ns, the temperature was raised 5K and equilibrated
-        again for 200 ns.
-        \item We continued raising the temperature by 5K and equilibrating for 200 ns
-        until the system was equilibrated for 200 ns at 320K.
-	\item The same process was repeated with a system equilibrated in Basin B and used
-	as a benchmark for comparison. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                % these next 2 figures are REALLY big (12-18M). Likely could reduce to near 0.5-1.0 MB without loss of 
-                % necessary resolution.  A few other figures could have resolution reduced.
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:340K_pore}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_tramp.png}
-                \caption{}\label{fig:p2p_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_tramp.png}
-
-                \caption{}\label{fig:thickness_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_tramp.png}
-                \caption{}\label{fig:order_tramp}
-        \end{subfigure}
-        \caption{(a) The open pore structure exhibited by a structure equilibrated
-        at 280K is characteristic of Basin A. (b) The closed pore structure with
-        a high degree of radial disorder exhibited when the structure in (a) is
-        heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
-        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
-        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
-        its uncertainty changes slope near 315K.}\label{fig:tramp}
-  \end{figure}
-
-  Basin A and Basin B are two configurationally metastable basins.
-  \begin{itemize}
-        \item There is litle change in disordered phase properties during the 
-        temperature ramp.
-	\item We observed smooth changes in order parameters as temperature
-        of the Basin A system was increased implying that we cannot claim the
-	existence of two phases (Figure~\ref{fig:phase_transition}).
-	\item Qualitatively, the pore structure of the Basin A system becomes
-        comparable to one characteristic of Basin B as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
-	\item The Basin A system does not converge to the same order parameter
-	values as Basin B, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
-	\item To resolve the quanitative discrepancy, we would need a slower 
-	temperature ramp
-	\item Since there are no abrupt changes in any order parameter along the 
-	trajectory, we can conclude that the two basins are not separate phases
-	\item Basin A is the closest match to what is seen experimentally
-	\item Basin B is likely an intermediate between the Col\textsubscript{h} 
-	phase and isotropic phase
-	\item Basin B is present in our simulations at lower temperatures 
-        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
-        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
-	because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
-	stabilize the system into Basin A. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-	% BJC: I'll get actual pictures of the system here. I'm not sure how 
-	% necessary this figure is though. It could go in the supplemental 
-	% information and I can reference the pictures in the previous figure
-	% since they show basically the same idea : Ordered vs. disordered pore
-	% Alternatively, I could show two diffraction patterns here from the 
-	% beginning and end temperature 
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:BasinA_280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:BasinB_340K_pore}
-        \end{subfigure}
-	\vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_layered.png}
-                \caption{}\label{fig:p2p_step}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_layered.png}
-
-                \caption{}\label{fig:thickness_step}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_layered.png}
-                \caption{}\label{fig:order_step}
-        \end{subfigure}
-        %MRS: Are (a) and (b) from the nonequilibrium short run?
-        %That's not clear. Not clear it's possible to state that it's
-        %the ``right'' disordered basin if from the end of a short heating run.
-	%BJC: They are from the short run, but as I comment above, I need to 
-	% replace them with the correct figures
-
-	\caption{In all cases, blue lines represent the measured value of
-	the order parameter, black lines are average values calculated from
-	equilibrated Basin B systems at each temperature, green shaded regions
-	represent the standard deviation of each of the black line values, and 
-	red dashed lines show where the temperature is bumped to the next level.
-	(a) At 280K, the system is in a configuration reminiscent of
-	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
-	spacing of Basin A decreases with temperature approaching the value 
-	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
-	temperature but is far from the Basin B value. Longer equilibrations at 
-	each temperature are needed to allow the system to fully expand. 
-        %MRS: might need to explain this ratio better?
-        (e) The ratio 
-	of pore radius to uncertainty for Basin A changes smoothly with temperature,
-	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
-  \end{figure}
-
-  \subsection*{Ionic conductivity calculation}
-
-  %MRS: which model? Be specific as to which of the above structural ensembles was used.
-  The model gives reasonable estimates of ionic conductivity when compared to 
-  experiment.
-  \begin{itemize}
-  	\item Calculated values of ionic conductivity obtained using the Nernst 
-	Einstein relation and Collective Diffusion model are compared in 
-	Table~\ref{table:conductivity}.
-	\item The two methods agree with each other within error, although the 
-	uncertainty obtained using the Collective Diffusion model is much higher.
-	\item Much longer simulations are needed to lower the uncertainty. % TODO: Run Basin B out longer at same conditions as A
-	\item Collective diffusion calculations were generated from 
-	500 ns simulations.
-	\item Our calculated values would benefit from longer simulations. 
-	\item For this reason we will likely only use the Nernst Einstein relation
-	in future calculations of this type. 
-	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
-	\item We hypothesize that conductivity is enhanced in Basin B due to a 
-	higher sodium ion diffusivity.
-	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
-	Sodium ions have less nearby sites to move to in Basin A.
-	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
-	\item In both cases, our calculated values for Basin A are higher than the 
-	experimental values, as expected. 
-	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
-	\item However, the real system, although mostly aligned and straight, has a 
-	distribution of azimuthal angles, meaning that the pores have a degree of 
-	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
-	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
-	fold increase in ionic conductivity. We would expect additional gains in a 
-	perfectly aligned system.
-  \end{itemize}
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
-  \hline
-  Method & Basin A & Basin B \\
-  \midrule
-  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
-  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
-  Experiment & \num{1.33e-5} (0.10) & -- \\
-  \bottomrule
-  \end{tabular}
-  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
-  agree within error. Both methods give calculated values of ionic conductivity which
-  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
-  \end{table}
-
-  %MRS: the next sections maybe should be supporting?
-  %MRS: you say ``the distance decreases by 1 A'' but is that true
-  %over all of the different structures? 
-  %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
-  %MRS: you don't otherwise discuss clearly what effect crosslinking would have. 
-  \subsection*{Implementation of the crosslinking algorithm}
-
-  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
-  Basin A.
-  \begin{itemize}  %BJC: working on the following. The following is what I expect
-  	\item There is an even distribution of crosslinks between same monomer tails, 
-	between monomers in the same pore and between monomers in different pores 
-	including periodic boundaries.
-	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
-	crosslinked
-	\item Major features are still present in the X-ray diffraction
-	\item The ionic conductivity is higher/lower in the crosslinked system
-  \end{itemize}
-  %BJC: THe following figure will be replaced with one representative of the new
-  % data I am  collecting above.
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
-		\caption{}\label{fig:p2p_diagram}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
-		\caption{}\label{fig:no_xlink_p2p}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{xlink_p2p.png}
-		\caption{}\label{fig:xlink_p2p}
-	\end{subfigure}
-	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
-	Each numbered circle represents a pore. Distances are measured along each of the 
-	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
-	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
-	individual pores in the crosslinked system are stable relative to the uncrosslinked
-	system}\label{fig:xlink}
-  \end{figure}
-
-  \section*{Conclusion}
-
-  We have used a detailed molecular model of the Col\subscript{h} phase formed by NA-GA3C11
-  in order to study the nanoscopic structure.
-  \begin{itemize}
-  	\item While there have been efforts to model formation of various liquid crystalline 
-	phases with molecular dynamics, to our knowledge there have been no studies which 
-	attempt to examine their structure with the same level of detail presented here.
-	\item We have confirmed that monomers stay partitioned in layers.
-	\item We were able to deduce that layers are composed of 5 monomers.
-	\item We have identified two metastable basins which each consist of a set of 
-	similar monomer configurations characterized by the degree of order in the pore region.
-	\item We verified that the basins are not separate phases.
-	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
-	membrane strucure. 
-	\item Simulated diffration patterns generated from MD trajectories suggest that
-	the offset configuration produces a structure with the closest match to experiment. 
-	\item Even though our model only answers these questions for a system created by 
-	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
-	little extra effort. 
-  \end{itemize}
-
-\clearpage
-\bibliography{llc}
-
 \end{document}

### 2017-09-22 Ben_Manuscripts/Paper1/Outline.tex
small change
addressed an issues compiling
organizing

@@
     Equilibration Scheme A:
+  \begin{itemize}
     \item Apply position restraints to aromatic rings in order to maintain
@@
 
-  We were inspired to ask question (4) when we observed that the initial distance
-  between layers can influence the approach towards equilibrium. 
+  In addition to the parallel displaced and sandwiched configurations we observed
+  that the initial distance between layers can influence the approach towards 
+  equilibrium.
   \begin{itemize}
   	\item Our choice of distance between layers results in long-term stability of 
-	different configurations indicating that we have found more than one metastable
-	free energy basin.
-  	\item Equilibrated systems built according to the 3.7 \angstrom~ 
-	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
-	open pore structure.
+	qualitatively different configurations suggesting that we have found more than
+        one metastable free energy basin.
+  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
+        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
+	structure.
         \item We will refer to this large set of configurations, with an open pore, as 
@@
 Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
-  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  patterns produced from equilibrated MD trajectories shows the most consistency
-  with the offset configuration in the OP basin.
+
+  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
+  %patterns produced from equilibrated MD trajectories shows the most consistency
+  %with the offset configuration in the OP basin.
+
+  We created systems using three 
+  distinct initial configurations and examined their structure by simulating 
+  X-ray diffraction patterns produced from equilibrated MD trajectories.
   \begin{itemize}
@@
 	\item For ease of reference, the third system will be referred to as Basin D (disordered). 
-%BJC: omit and call it basin B
-%MRS or just be consistent from the beginning.  Or call Basins O and D          
 	\item The three systems were equilibrated according to our procedure with
@@
 	Figure ~\ref{fig:XRDsim}. 
-	%BJC: maybe break into a separate paragraph starting here
+  \end{itemize}
+
+  % Three paragraphs instead here? Talk about disordered, parallel displaced and 
+  % layered separately? Try it. 
+  % Talk about disordered last so it leads in to 
+  % Also maybe don't talk about question 4 until after this
+  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
+  patterns shows the most consistency with the offset configuration in the OP basin.
+  \begin{itemize}
+        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
+	R-$\pi$ and R-spots are not present. 
+        \item Simulated XRD of the sandwiched configuration contains all features 
+        except for R-helix.
+        \item Most notably, R-spots appears in the expected location, which suggests 
+        that there is something intrinsic to the sandwiched packing that gives rise 
+        to such features.
+
 	\item The equilibrated parallel displaced structure exhibits R-alkanes and
@@
 	\item Due to low resolution, making out the individual spots of R-pores is
-	challenging and can be validated upon full spherical integration of the 3D 
-	structure factor. However, the same information can be extracted by measuring 
-	the pore spacing as described earlier.
+	challenging and can be validated with slightly better resolution upon full
+	spherical integration of the 3D structure factor. However, the same 
+	information can be extracted by measuring the pore spacing as described earlier.
 	\item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
@@
 	to such features. 
-	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
-	R-helix, R-$\pi$ and R-spots are not present.
   \end{itemize}
@@
 	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
-	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.
+	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.i
+	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
+        that the spots arise as a consequence of the tails. 
 	\item By removing atoms from the trajectory and simulating a diffraction 
@@
 	\item The distribution of these angles is consistent with the location of 
-	the spots (Figure~\ref{fig:angle_distribution}).
-	\item We reason that monomer tails stacked closely in the sandwiched conformation
-	are forced to splay apart and pack in between in each other which creates a
-	nearly hexagonal array of packed tails. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\hspace{-1cm}
-		\vspace{1cm}
-		\includegraphics[width=\textwidth,scale=2]{tails_topview.png}
-		\caption{}\label{fig:tails_topview}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{tails_rzplot.png}
-		\caption{}\label{fig:tails_rzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{centroids_box.png}
-		\caption{}\label{fig:centroids}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{angles_traj_layered.png}
-		\caption{}\label{fig:angle_distribution}
-	\end{subfigure}
-	\caption{(a) The trajectory can be stripped of all atoms except carbon
-	atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
-	still gives rise to R-spots. (c) Finding the center of mass and visualizing 
-	their coordinates reveals the hexagonal-like packing of the tails. (d) The 
-	distribution created by measuring the angle between each centroid (e.g. red 
-	in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
-	plane has distinct spikes near 30\degree, which is consistent with the location
-	of R-spots}\label{fig:tail_packing}
+	the spots (Figure~\ref{fig:tail_packing}).
+	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
+	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
+	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
+	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
+        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
+        is a reconcilable difference with our simulated results.  
+  \end{itemize}
+
+  \begin{figure}[ht]
+  \centering
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{offset_tail_packing.png}
+        \caption{}~\label{fig:offset_tails}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{angles_traj_layered.png}
+        \caption{}~\label{fig:layered_tails}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{integrated_WAXS_ring.png}
+        \caption{}~\label{fig:rz_layered}
+  \end{subfigure}
+  \caption{The distribution of angles w.r.t. xy plane between alkane chain tail centroids and nearest
+  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (b) configurations both show
+  distinct peaks at $\pm$ 33 $\degree$. (c) Integrated 2D WAXS data between $q_r$=1 and $q_r$=1.42 shows
+  distinct peaks at with maxima at $\pm$ 37 $\degree$}~\label{fig:tail_packing}
   \end{figure}
+
   %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
@@
   %MRS: I think things have changed since then? 
+  The disordered basin shares little in common with the ordered basin but 
+  its long term stability suggests that it can exist under some conditions.  
+  Basin B is the dominant configuration at higher temperatures.
+  \begin{itemize}
+        \item We linearly ramped the temperature of a system in Basin A
+        from 280K to 340K over 100 ns.
+        \item Visually, there is a distinct change in pore structure from one
+        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
+        Basin B (Figure~\ref{fig:340K_pore}).
+        \item The slope of all order parameters changes between 315K and 325K
+        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
+        possibility of an abrupt change in system ordering.
+        \item Our 100 ns temperature ramp was likely too fast and caused the system
+        to suffer from hysteresis.
+  \end{itemize}
+
   We can not immediately classify Basin A and Basin B as separate phases.
@@
         the degree to which monomers obstruct the pore region.
-  \end{itemize}
-
-  Basin B is the dominant configuration at higher temperatures.
-  \begin{itemize}
-	\item We linearly ramped the temperature of a system in Basin A 
-	from 280K to 340K over 100 ns.
-        \item Visually, there is a distinct change in pore structure from one
-        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
-        Basin B (Figure~\ref{fig:340K_pore}).
-        \item The slope of all order parameters changes between 315K and 325K
-	(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
-        possibility of an abrupt change in system ordering.
-        \item Our 100 ns temperature ramp was likely too fast and caused the system
-        to suffer from hysteresis.
   \end{itemize}
@@
 
-  We have used a detailed molecular model of the Col\subscript{h} phase formed by NA-GA3C11
+  We have used a detailed molecular model of the Col\textsubscript{h} phase formed by NA-GA3C11
   in order to study the nanoscopic structure.

### 2017-09-22 HII/Scripts/tail_packing.py

@@ -178,20 +178,34 @@ if __name__ == "__main__":
         print("Loading saved arrays")
         arrays = np.load('angles_ld_%s.npz' % args.suffix, encoding='bytes')
         angles = arrays['angles']
+        centroids = arrays['centroids']
+        atoms_per_frame = int(angles.shape[0] / centroids.shape[0])
+        angles = angles[args.start * atoms_per_frame : args.end * atoms_per_frame]
         ld = arrays['ld']
         nlist = arrays['nlist']
-        centroids = arrays['centroids']
 
     if args.write_gro:
         file_rw.write_gro_pos(centroids[-1, :, :], 'centroids.gro', name='NA')
 
     angles = [value for value in angles if not math.isnan(value)]
 
-    nbins = 45
+    nbins = 180
     (counts, bins) = np.histogram(angles, bins=nbins)
-    plt.hist(angles, bins=nbins)
-    plt.show()
+    # plt.hist(angles, bins=nbins)
+    # plt.show()
+
     bin_width = bins[1] - bins[0]
+    db = bin_width
+    bin_centers = [bins[i - 1] + ((bins[i] - bins[i - 1]) / 2) for i in range(1, len(bins))]
+    integrated_area = np.trapz(counts, bin_centers)  # integrated area of histogram for normalization
+    avg = counts * bin_width / integrated_area
+
+    max1 = np.max(avg[int((-bins[0] - 40)/db):int((-bins[0] - 20)/db)])
+    max2 = np.max(avg[int((-bins[0] + 25)/db):int((-bins[0] + 50)/db)])
+    print(np.where(avg == max2))
+    print(90 - np.where(avg == max1)[0][0]*db)
+    print(-90 + np.where(avg == max2)[0][1]*db)
+    print(max1, max2)
 
     plt.figure()
     bin_centers = [bins[i - 1] + ((bins[i] - bins[i - 1]) / 2) for i in range(1, len(bins))]
@@ -201,8 +215,8 @@ if __name__ == "__main__":
     plt.ylabel('Normalized frequency', fontsize=14)
     plt.axes().tick_params(labelsize=14)
     plt.tight_layout()
-
-
+    plt.show()
+    exit()
     if args.fit:
         bin_locations = np.linspace(-90, 90, nbins)
         fapprox = np.array([f(t, 8, 180, bin_locations).real for t in counts]) + np.mean(bins)

### 2017-09-25 Ben_Manuscripts/Paper1/Outline.tex
lots of reorganization

@@
     \item \textit{RO membranes}
-    \item \textbf{Inconsistent performance} : Current state-of-the-art RO membranes are unstructured with
+    \item Inconsistent performance : Current state-of-the-art RO membranes are unstructured with
     tortuous and polydisperse diffusion pathways which leads to 
     inconsistent performance \cite{song_nano_2011}
-    \item \textbf{High energy requirements} : Necessarily high feed pressures 
+    \item High energy requirements : Necessarily high feed pressures 
     drive up energy requirements which strains developing regions and
     contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
-    \item \textbf{Separation based on differences in solubility and diffusivity}:
+    \item Separation based on differences in solubility and diffusivity:
     Moreover, designing RO membranes to achieve targeted separations of 
@@
     \item NF is often used as a precursor to reverse osmosis
-    \item Unfortunately, NF membranes, like RO, are produced with a pore size 
+    \item Unfortunately, NF membranes, like RO, possess a pore size 
     distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
@@
   \begin{itemize}
-    \item \textbf{Tune size and functionality of building blocks} to control pore
+    \item Tune size and functionality of building blocks to control pore
     size and shape: One can accomplish targeted separations with high 
@@
     \item As a result, solute rejecting pores can have their sizes tuned
-    uniformly, resulting in \textbf{strict size cut-offs}.
-    \item Entirely \textbf{different mechanisms} may govern transport in a given
+    uniformly, resulting in strict size cut-offs.
+    \item Entirely different mechanisms may govern transport in a given
     nanostructured material which can inspire novel separation techniques.
@@
   \begin{itemize}
-    \item \textbf{Graphene sheets} are atomically thick which results in excellent
+    \item Graphene sheets are atomically thick which results in excellent
     permeability but defects during manufacturing severely impact 
     selectivity. \cite{cohen-tanugi_multilayer_2016}
-    \item Molecular dynamics simulations of \textbf{carbon nanotubes} show
+    \item Molecular dynamics simulations of carbon nanotubes show
     promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
     unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
-    \item \textbf{Zeolites} have sub-nm pores with a narrow pore size 
+    \item Zeolites have sub-nm pores with a narrow pore size 
     distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
@@
     \item LLCs share the characteristic ability of nanostructured membrane
-    materials to create \textbf{highly ordered structures} with the added benefits
-    of \textbf{low cost} and synthetic techniques feasible for 
-    \textbf{large scale production} \cite{feng_scalable_2014}
+    materials to create highly ordered structures with the added benefits
+    of low cost and synthetic techniques feasible for 
+    large scale production \cite{feng_scalable_2014}
     \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
@@
 %     space} available for membrane design  %BJC: redundant
+    \item Over the past 20 years, HII phase LLC membrane studies have been limited primarily
+    to Na-GA3C11 with some characterization done after minor structural modifications
+    \cite{resel_structural_2000}.
+    \item Rejection studies show that this membrane can not perform separations of
+    solutes less than 1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
     \item  We do not yet understand how to reduce the effective pore size or 
@@
     desalination or small organic molecule separations.
-    \item Rejection studies show that this membrane can not perform separations of
-    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
-    \item Over the past 20 years, LLC membrane studies have been limited primarily 
-    to Na-GA3C11 with some characterization done after minor structural modifications
-    \cite{resel_structural_2000}. 
-    \item Optimization has been performed through trial and error. The only source of 
-    predictive modeling has been macroscopic models which likely do not adequately describe 
-    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
-    \item It will be challenging to efficiently narrow down the design space in 
-    a laboratory setting.
+    \item It will be challenging to efficiently narrow down the large design space in 
+    a laboratory setting without a robust model.
+    \item The only source of predictive modeling has been macroscopic models 
+    which likely do not adequately describe transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
+    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
+    \item Choice of counterion may influence the establishment of a Donnan potential
+    affecting the degree to which the membrane can exclude charged species.
     \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
@@
     membrane design.
-    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
-    \item Choice of counterion may influence the establishment of a Donnan potential 
-    affecting the degree to which the membrane can exclude charged species.
-    \item Moieties inside the pores may interact with neutral solutes, rejecting
-    on the basis of shape and 
-    %MRS: size pretty much is hydrodynamic radius
-    %size, 
-    interactions with specific chemical groups
-rather than just hydrodynamic radius.
-    %MRS: isn't this next point just a restatement of what was said at the top?
-    %BJC: yes, deleted
-  \end{itemize}
-
-  Our approach to constructing a general model will be based on the development of a
-  model of a specific LLC membrane which has ample experimental characterization. %BJC: ample too much?
+    \item Molecular dynamics will have the required level of detail
+  \end{itemize}
+
+  Our approach to constructing a general model will follow the development of a
+  model of a specific LLC membrane with sufficient experimental characterization. %BJC: ample too much?
     \begin{itemize}
@@
 	    \item Despite having structural data, there is still information which 
-	    experiment cannot definitively answer
+	    experiment cannot definitively answer.
     \end{itemize}
@@
 
-  To further understand the nanoscopic structure of these membranes, there
-  are several key questions which we intend to answer and will be laid out 
-  and numbered in subsequent paragraphs.
+  Despite having structural data, there is still information which 
+  experiment cannot definitively answer. There are several key 
+  questions that we intend to answer which will be laid out and numbered
+  in subsequent paragraphs.
 
@@
 	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
-	\item (1) Do monomers partition into and persist as defined monomer layers?
   \end{itemize}
@@
   There has been no definitive answer to the question in literature.
-%   We do not know the number of monomers that constitute the layers which stack
-%   on top of each other to create pores.
-  \begin{itemize}
-%     \item The Col\textsubscript{h} phase is described as having pores made of
-%     disks or layers stacked on top of one another, each containing a set 
-%     number of monomers. 
-    \item A simple simulation study of a similar molecule 
-%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.
-I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context.
-We thought they did something reasonable, but they really didn't.
-%suggests
-%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
-suggested
+  \begin{itemize}
+    \item A simple molecular simulation study of a similar molecule suggested
     that there are 4 monomers in each layer. Their estimation is based on a
@@
     that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-    \item A molecular model has the best chance of directly answering this question.
-  \end{itemize}
-%MRS: phrasing
-    %\item Once we know the number of monomers in each layer, we still do not know how
+    \item A molecular model orders of magnitude larger than any other reported atomistic 
+    liquid crystal membrane simulations has the best chance of directly answering this question.
+  \end{itemize}
 
@@
       \cite{waller_hybrid_2006,ringer_effect_2006}.
+      \item We can use simulated X-ray diffration patterns to compare the two 
+      stacking configurations. 
    \end{itemize}
@@
     are kinetically trapped in a metastable free energy basin
-    \item We must be able to identify which state is produced experimentally
-  \end{itemize}
-
-  We must show that the developed molecular model is consistent with
-  physical observations so that we can rely on conclusions drawn about
-  structural features characteristic of the system.
-  \begin{itemize}
-    %MRS: main finding shouldn't be the model, but the things learned from the model. New suggestion below.
-    %\item This article will illustrate the development of a predictive molecular model 
-    %and the steps taken to ensure it mimics the real system within the constraints 
-    %inherent to MD.
+    \item We must be able to identify which state is produced experimentally and 
+    why others are not.
+  \end{itemize}
+
+  Once we have addressed all of the above questions, we must show that the 
+  developed molecular model is consistent with physical observations so that we
+  can rely on conclusions drawn about structural features characteristic of 
+  the system.
+  \begin{itemize}
     \item In this study, we build a significantly more realistic atomistic model of LLC membranes 
@@
     and what structure hypotheses are supported by this model.
-
-    %MRS: this is kind of understood -- rephrasing?
-    %\item To understand how physically realistic the model is, validation by comparison
-    %to experiment is necessary. 
     \item We validate the model using as much experimental information as possible.
-    \item We are %primarily 
-    most interested in reproducing the 
-    conclusions about structure which have been made from X-ray diffraction (XRD) 
-    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
-    \begin{itemize}
-    %MRS: these are really supporting items to the above: put them indented.
-	    \item We have comparied simulated X-ray diffraction patterns to experiment in 
+    \item We are most interested in reproducing the conclusions about structure
+    which have been made from X-ray diffraction (XRD) experiments and in matching ionic
+    conductivity measurements~\cite{feng_thin_2016}.
+    \begin{itemize}
+	    \item We have compared simulated X-ray diffraction patterns to experiment in 
 	    order to match major features present in the 2D patterns.
@@
     \end{itemize}
-    %\item We have created a model that can be used to probe the large design space
-    % available for membrane design
     \item The structure-building approach and analysis used in this paper can be readily extended
@@
 
-  HII monomers were parameterized using the Generalized AMBER Forcefield
+  Liquid crystal monomers were parameterized using the Generalized AMBER Forcefield
   \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
@@
     \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
-    % MRS: how chosen? randomly? be precise
-    % BJC: added randomly to bullet point below
     \item A low energy configuration was randomly pulled from the trajectory
@@
     \item To bypass the slow self-assembly process, python scripts are used
-    to assemble monomers into a structure close 
-    %MRS:
-    %to the expected equilibrium configuration. 
-    to one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
-    %\item A short, restrained equilibration, followed by NPT simulations 
-    %between 400 and 500 ns, allows the initial configuration to relax into
-    %an equilibrium configuration.
-    %\item Our logic for choosing a starting configuration and the details
-    %of the equilibration schemes are presented below.
-   \end{itemize}
-
-  We tested a number of equilibration schemes in an effort to match experiment
-  while overcoming kinetic limitations of such a large system that can easily
-  get stuck in multiple metastable states.
-    Equilibration Scheme A:
-  \begin{itemize}
-    \item Apply position restraints to aromatic rings in order to maintain
-    orientational order. 
-    \item A short, restrained equilibration, followed by NPT simulations 
-    between 400 and 500 ns, allows the initial configuration to relax into
-    an equilibrium configuration.
-    \item Our logic for choosing a starting configuration and the details 
-    of the equilibration schemes are presented below.
+    to assemble monomers into a structure close to one of a number of 
+    hypothesized equilibrium configurations (Figure~\ref{fig:python}).
    \end{itemize}
@@
 I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense.
-And it doesn't make sense to talk about XRD this early in the methods.
-  \end{itemize}
-
-  We chose initial guesses for the remaining structural parameters based on 
+And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
+    \item We chose initial guesses for the remaining structural parameters based on
     experimental data and treated them as variables during model development.
-  %BJC: I could potentially break this paragraph into smaller paragraphs centered around
-  % the bolded structural parameters
-  %MRS Breaking into more structure is good. Short sentences, only 3-5 sentences per paragraph.
-
-    %MRS: initial distance between pores -- we set the initial, and let it find where it wants to be
-    %MRS: Or is this the initial data we COMPARE to? Be more specific about the use of these numbers. The use of the data needs to be clarified, since it's main effort here. 
-  We placed pores at a chosen initial spacing, then allowed the system to settle 
-  into its preferred spacing. 
-  \begin{itemize}
-    \item Our chosen distance between pores was based on experimental SAXS data for
-    this system \cite{feng_thin_2016}.
+  \end{itemize}
+
+  We used experimental wide angle X-ray scattering (WAXS) data (produced as described 
+  in~\cite{feng_scalable_2014}) and small angle X-ray scattering (SAXS) data from~\cite{feng_thin_2016}
+  to inform some of our initial guess choices (Figure~\ref{fig:SWAXS}). We rely primarily
+  on the 2D WAXS data since it encodes all structural details down to the sub-nm scale.
+  \begin{itemize}
+        \item There are five major features of interest present in the 2D experimental
+        pattern shown in Figure~\ref{fig:WAXS}.
+        \item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
+        corresponding to a real spacing of 3.7 \angstrom~. The reflection is
+        attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
+        perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
+        reflection will be referred to as R-$\pi$.
+        \item A weak intensity line is located at exactly half the $q_z$ value of
+        R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a
+        real space periodic spacing of 7.4 \angstrom~. This reflection has been
+        interpreted  as 2\textsubscript{1} helical ordering of aromatic rings
+        along the z axis meaning if the positions of the aromatic rings can
+        be traced by a helix, then for each turn in the helix, there should be
+        two aromatic rings. For this reason it will be referred to as R-helix.
+        \item A third major reflection is marked by a low intensity ring located
+        at r = 1.4 \angstrom$^-1$. The real space separation
+        corresponds to 4.5 \angstrom~ which is characteristic of the average
+        spacing between packed alkane chains. This reflection will be called R-alkanes.
+        \item Within R-alkanes, are four spots of higher intensity which
+        will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
+        in their respective quadrants. In many liquid crystal systems this can be
+        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
+        \item The first corresponds to the spacing and symmetry of
+        the d\textsubscript{100} plane which can be related to the distance between
+        pores. The feature, which will be called R-pores, is characterized by dots
+        along $q_z$ = 0. The spacing between dots is indicative of the hexagonal
+        symmetry of the packed pores. The same information is obtained using a SAXS
+        setup. By radially integrating the 2D data one gets a 1D curve which is 
+        shown in Figure~\ref{fig:SAXS}.  % BJC: I also have 2D SAXS data
+  \end{itemize}
+
+  \begin{figure}[!ht]
+        \centering
+        \begin{subfigure}[t]{0.43\linewidth}
+                \centering
+        %       \vspace{12mm}
+                \includegraphics[width=\linewidth]{SAXS.png}
+                \caption{}\label{fig:SAXS}
+        \end{subfigure}
+        \begin{subfigure}[t]{0.47\linewidth}
+                \centering
+                \raisebox{.2\textwidth}{%
+                \includegraphics[width=\linewidth]{WAXS_soft_confined.png}
+                }
+                \caption{}\label{fig:WAXS}
+        \end{subfigure}
+        \caption{(a) 2D wide angle X-ray scattering gives details about repeating
+        features less than 1 nanometer apart. (b) 1D small angle X-ray scattering
+        indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
+  \end{figure}
+
+%  We chose an initial layer spacing based on experimental 2D WAXS data.
+%  \begin{itemize}  
+%    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
+%    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
+%    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
+%    \item Our simulations tend to equilibrate to a wider interlayer spacing of
+%    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
+%    spacings greater than 4 \angstrom~.
+%  \end{itemize}
+
+  We chose an initial layer spacing based on R-$\pi$.
+  \begin{itemize}  
+    \item Each monomer was rotated so the plane of the aromatic ring on the
+    head groups would be parallel to the xy plane.
+    \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
+    apart in the z-direction.
+    \item Our simulations tend to equilibrate to a wider interlayer spacing of
+    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
+    spacings greater than 4 \angstrom~.
+  \end{itemize}
+
+  We placed pores at a chosen initial spacing based on R-pores, then allowed
+  the system to settle into its preferred spacing. 
+  \begin{itemize}
     %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
@@
     respective pores.
-    \item Statistics were generated using the bootstrapping technique.
+    \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
     %BJC: Do bootstrapping details go in supplemental?
+    	% Supplemental vvvv
+	\begin{itemize}
     	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
@@
         a perfect hexagonal array. Only 4 are independent  
-  \end{itemize}
-
-  %MRS: initial layer spacing.
-  We chose a layer spacing based on experimental 2D WAXS data.
-  \begin{itemize}  
-    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
-    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
-    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
-    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
-    spacings greater than 4 \angstrom~.
+        % Supplemental ^^^^
+	\end{itemize}
   \end{itemize}
@@
   \begin{itemize}
-    \item Experimental evidence suggests uniform pores with radii of 0.6 nm a pore radius
-    \item Comparing a geometric measurement of pore size derived from an 
-    atomistic model, to a less precise, experimentally derived pore size estimate,
-    will give ambiguous results.
-    \item What is meant by pore radius will not be clear until we have a clear picture
+    \item Experimental evidence suggests uniform pores with radii of 0.6 nm 
+    \item Comparing a geometric measurement of pore size derived from an atomistic model,
+    to a less precise, experimentally derived pore size estimate, will give ambiguous results.
+    \item What is meant by pore radius will not be clear until we establish a clear picture
     of the nanoscopic pore environment.
-    \item Atomistic simulations do a good job of providing the level of detail we need. The challenge
-    will be to ensure that we are producing the correct picture.
-    %MRS: point out this is one of the things that atomistic simulation can actually do very well - 
-    % provide a clear picture of a nanoscopic environment (the questions is whether it's 
-    % providing the _right_ clear picture).
     \item When constructing pores, we chose the carboxylate carbon from the monomer
     head group as a reference atom, and placed it a distance r from the pore center,
-    where r is the pore radius.  %BJC: figure making that clear
+    where r is the pore radius. (See Supplemental Information) %BJC: figure making that clear
     \item We will not make direct comparisons of pore radius between our model 
-    and experiment to avoid the ambiguity. 
-    \item However, we do define a pore radius based for our own purposes.
-    \item Pore radius was measured by calculating the distance between the center of 
-    mass of each aromatic ring and the center of mass of all aromatic rings in their 
-    respective pores.
-  \end{itemize}
-
-  %MRS: OK, this is a variable again that we need to set. 
-  The \textbf{relative interlayer orientation} was chosen based on clues from 
+    and experiment to avoid the ambiguity, however, we do define a pore radius based 
+    for our own purposes.
+    \item To measure the pore radius in our model we calculate the distance between 
+    the center of mass of each aromatic ring and the center of mass of all aromatic rings
+    in their respective pores.
+  \end{itemize}
+
+  The relative interlayer orientation was chosen based on clues from 
   diffraction data as well as the various known stacking modes of benzene 
@@
     stacking modes will be explored.
+    \item Both have reported stacking distances near 3.7 \angstrom
     %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
@@
 
+  % This can be cut down if C and D prove to be no help. 
   We tested a number of equilibration schemes of increasing complexity in an effort
-  to match experiment while overcoming kinetic limitations of such a large system 
-  that can easily get stuck in multiple metastable states. All start from an initial
-  configuration generated with chosen structure variables. 
+  to match experiment while overcoming kinetic limitations that might trap the system 
+  in a metastable states. All start from an initial configuration generated with 
+  chosen structure variables. 
   \begin{itemize}
@@
 
-  % The following methodology is taken from the 2014 Feng et al. paper where
+  % BJC: The following methodology is taken from the 2014 Feng et al. paper where
   % WAXS is reported. The data we are using comes from the 2016 paper which 
@@
   % however I will likely reproduce it with matplotlib
-  Experimental wide angle X-ray scattering measurements were performed using a 
-  Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
-  ($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
-  calibrations of the resultant 2-D WAXS patterns were done by using a 
-  silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
-  patterns were integrated into 1-D plots of scattering intensity (I) versus
-  q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
-  2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.
+
+  %\Experimental wide angle X-ray scattering measurements were performed using a 
+  %Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
+  %($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
+  %calibrations of the resultant 2-D WAXS patterns were done by using a 
+  %silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
+  %patterns were integrated into 1-D plots of scattering intensity (I) versus
+  %q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
+  %2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.
 
@@
     %MRS: state how you decided which was the linear region.
-    %BJC: nothing fancy other than looking at the msd plot and determing where to
+    %BJC: nothing fancy other than looking at the msd plot and determining where to
     % start fitting. I suppose I could minimize R^2 but that seems like overkill
@@
     \item Ion concentration was measured with respect to the entire unit cell. 
-    %BJC: I don't think this needs to be said
-    %MRS: probably - people might think of conduction just occurring in the pore, so clarity is good. Could potentially have a figure illustrating the two ways of calculating conductance?  
     \item The second method, termed the 'Collective Diffusion' model, measures 
@@
     be calculated using the einstein relation.
-    %MRS: might need a bit more mathematical description of what is done here. For example explicitly stating that the D is 
-    % the diffusion coefficient of the variable Q, which is the center of the charge (I think?)
-    %BJC: yea its the center of charge since I add all of the charges together. I added something to the effect of what you are saying. Also put the equation earlier.
     \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
-    %MRS: still want to state it clearly.   
   \end{itemize}
@@
   We will now address the questions raised in the introduction in the order
-  that they were asked.
+  that they were asked.  %BJC: I dont like this
 
@@
   the length of the pores (Fig~\ref{fig:zdf}).
+  % BJC: add how this calculation is done to methods section (put where I talk about
+  % choosing distance between layers
   \begin{itemize}

### 2017-09-26 Ben_Manuscripts/Paper1/Outline.tex
zdf methodology

@@
   Our approach to constructing a general model will follow the development of a
-  model of a specific LLC membrane with sufficient experimental characterization. %BJC: ample too much?
+  model of a specific LLC membrane with sufficient experimental characterization.
     \begin{itemize}
@@
         along $q_z$ = 0. The spacing between dots is indicative of the hexagonal
-        symmetry of the packed pores. The same information is obtained using a SAXS
+        symmetry of the packed pores. The same information at higher resolution is obtained using a SAXS
         setup. By radially integrating the 2D data one gets a 1D curve which is 
@@
 
-  We chose an initial layer spacing based on R-$\pi$.
-  \begin{itemize}  
-    \item Each monomer was rotated so the plane of the aromatic ring on the
-    head groups would be parallel to the xy plane.
+  We chose the initial layer spacing based on R-$\pi$.
+  \begin{itemize}  
+    \item Each monomer was rotated so the plane of the aromatic head groups would
+    be parallel to the xy plane.
     \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
     apart in the z-direction.
+    \item We extracted the equilibrium distance between layers based on the first
+    peak of a spatial correlation function, $g(z)$, measured along the z-axis (perpendicular to 
+    the membrane plane)
+    \item To calculate $g(z)$, we binned the z component distances between 
+    the center of mass of each benzene ring and all others of the same pore 
+    over 50 ns of equilibrated trajectory and then normalized by the average
+    number density.
     \item Our simulations tend to equilibrate to a wider interlayer spacing of
@@
     stacking modes will be explored.
-    \item Both have reported stacking distances near 3.7 \angstrom
+    \item Both have reported stacking distances near 3.7 \angstrom % Reference
+    \item Headgroups in the sandwiched configuration are stacked directly on top of
+    each other while stacked headgroups in the parallel displaced configuration are offset 
+    by $180/nmon$ degrees where $nmon$ equals the number of monomers per layer.
     %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
@@
   %to stack the layers, and how to orient them with respect to each other.
-  %\begin{itemize}
+  %\begin{itemize
   %	\item To verify our choices for each parameter, we compare our calculations

### 2017-09-26 Ben_Manuscripts/Paper1/Outline.tex
More organization

@@
   We will now address the questions raised in the introduction in the order
-  that they were asked.  %BJC: I dont like this
+  that they were asked.  %BJC: Not a fan of this
 
@@
 
+  % BJC: might replace with a figure containing alllllll of the zdf's
+  \begin{figure}[!ht]
+        \centering
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf5layered.png}
+                \caption{}\label{fig:zdf_layered}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf5offset.png}
+                \caption{}\label{fig:zdf_offset}
+        \end{subfigure}
+        \caption{Pair distribution functions of aromatic carbons for the
+        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
+        parallel displaced configurations. Clear periodic maxima in the 
+        $z$ probability density indicate distinct layers. The magnitude 
+        of the spikes with respect to the average suggest that the 5 
+        monomer per layer, sandwiched configuration possesses a higher 
+        degree of layer partitioning.}\label{fig:zdf}
+  \end{figure}
+
   To discern the composition of the monomer layers, addressing (2), we ran 
@@
   	\item Both the sandwiched and parallel displaced configurations were tested.
-	\item All systems are stable after 50 ns of simulation.  % BJC: edited this for clarity
+	\item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
         %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
-        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
-        %MRS: remind people where the uncertainty comes from.
-	%BJC: It looks like the 7 and 8 monomer systems were only run for 50 ns.
-The 4 monomer system was run for 200 ns.
-5 and 6 have a lot of data.
-7 and 8 flattened pretty quickly, so at the time I figured it wasn't worth continuing.
-But I'll extend them just to be thorough.
+	%BJC: Working on getting them all run out to 400 ns
 	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
-	Systems built with 5 monomers in each layer equilibrate to a pore spacing
+	\item Systems built with 5 monomers in each layer equilibrate to a pore spacing
 	that is most consistent with the experimental value of 4.12 nm derived from
@@
   \end{itemize}
+
+  % BJC: Even though I will shift focus to only 5 monomers per layer, I can put other data
+  % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information
 
@@
   \end{tabular}
-  \caption{The pore spacing 
-  %MRS added
-  (given in \angstrom~)
-  of the model increases as number of monomers
-  in each layer increases. The pore spacing of a system starting in the 
-  sandwiched configuration is systematically lower than that started in an 
-  offset configuration. Systems built with 5 monomers per layer in a parallel
-  displaced configuration result in a pore spacing closest 
-  %MRS: clarified.
-  %to experimental data
-  to the experimental 4.12 \angstrom~}\label{table:p2p} 
+  \caption{The pore spacing (given in $\nm$) of the model increases as
+  number of monomers in each layer increases. The pore spacing of a system
+  starting in the sandwiched configuration is systematically lower than 
+  that started in an offset configuration. Systems built with 5 monomers
+  per layer in a parallel displaced configuration result in a pore spacing
+  closest to the experimental 4.12 $\nm$~}\label{table:p2p} 
   \end{table}
 
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5layered.png}
-		\caption{}\label{fig:zdf_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5offset.png}
-		\caption{}\label{fig:zdf_offset}
-	\end{subfigure}
-	\caption{Pair distribution functions of aromatic carbons for the
-	(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, 
-	parallel displaced configurations. 
-        %MRS: added some info.
-        Clear periodic maxima in the $z$ probability density indicate
-        % Spikes in the distribution mark
-	distinct layers. The magnitude of the spikes with respect to the 
-	average suggest that the 5 monomer per layer, sandwiched configuration
-	possesses a higher degree of layer partitioning.}\label{fig:zdf}
-  \end{figure}
-
-  To answer question (3) we require high resolution experimental evidence which we 
-  can match to our simulations. Experimental WAXS measurements encode all structural
-  details and we would like to match them as well as possible. 
-  %MRS: also encodes the pore spacing
-  %BJC: got rid of 'remaining' in 'remaining structural details'
-  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
-  \begin{itemize}
-  	\item There are five major features present in the 2D experimental 
-	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
-	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
-	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
-	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-	perpendicular to the membrane plane, or z-axis. For simplicity, this 
-	reflection will be referred to as R-$\pi$.
-        %MRS: why R in R-pi? for reflection?
-	%BJC: yes, R = reflection
-	\item A weak intensity line is located at exactly half the $q_z$ value of
-	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
-	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
-	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
-	along the z axis meaning if the positions of the aromatic rings can
-	be traced by a helix, then for each turn in the helix, there should be
-	two aromatic rings. For this reason it will be referred to as R-helix.
-	\item A third major reflection is marked by a low intensity ring located
-	at r = 1.4 \angstrom$^-1$. The real space separation 
-	corresponds to 4.5 \angstrom~ which is characteristic of the average 
-	spacing between packed alkane chains. This reflection will be called R-alkanes.
-	\item Within R-alkanes, are four spots of higher intensity which 
-	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
-	in their respective quadrants. In many liquid crystal systems this can be
-	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
-	\item The final major reflections correspond to the spacing and symmetry of 
-	the d\textsubscript{100} plane which can be related to the distance between
-	pores. The feature, which will be called R-pores, is characterized by dots 
-	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
-	symmetry of the packed pores. It is easiest to interpret the data by 
-	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}[t]{0.47\linewidth}
-		\centering
-		\raisebox{.2\textwidth}{%
-		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-		}
-		\caption{}\label{fig:WAXS}
-	\end{subfigure}
-	\begin{subfigure}[t]{0.43\linewidth}
-		\centering
+%  To answer question (3) we require high resolution experimental evidence which we 
+%  can match to our simulations. Experimental WAXS measurements encode all structural
+%  details and we would like to match them as well as possible. 
+%  %MRS: also encodes the pore spacing
+%  %BJC: got rid of 'remaining' in 'remaining structural details'
+%  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
+%  \begin{itemize}
+%  	\item There are five major features present in the 2D experimental 
+%	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
+%	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
+%	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
+%	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
+%	perpendicular to the membrane plane, or z-axis. For simplicity, this 
+%	reflection will be referred to as R-$\pi$.
+%       %MRS: why R in R-pi? for reflection?
+%	%BJC: yes, R = reflection
+%	\item A weak intensity line is located at exactly half the $q_z$ value of
+%	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
+%	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
+%	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
+%	along the z axis meaning if the positions of the aromatic rings can
+%	be traced by a helix, then for each turn in the helix, there should be
+%	two aromatic rings. For this reason it will be referred to as R-helix.
+%	\item A third major reflection is marked by a low intensity ring located
+%	at r = 1.4 \angstrom$^-1$. The real space separation 
+%	corresponds to 4.5 \angstrom~ which is characteristic of the average 
+%	spacing between packed alkane chains. This reflection will be called R-alkanes.
+%	\item Within R-alkanes, are four spots of higher intensity which 
+%	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
+%	in their respective quadrants. In many liquid crystal systems this can be
+%	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
+%	\item The final major reflections correspond to the spacing and symmetry of 
+%	the d\textsubscript{100} plane which can be related to the distance between
+%	pores. The feature, which will be called R-pores, is characterized by dots 
+%	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
+%	symmetry of the packed pores. It is easiest to interpret the data by 
+%	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
+%  \end{itemize}
+
+%  \begin{figure}[!ht]
+%	\centering
+%	\begin{subfigure}[t]{0.47\linewidth}
+%		\centering
+%		\raisebox{.2\textwidth}{%
+%		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
+%		}
+%		\caption{}\label{fig:WAXS}
+%	\end{subfigure}
+%	\begin{subfigure}[t]{0.43\linewidth}
+%		\centering
 	%	\vspace{12mm}
-		\includegraphics[width=\linewidth]{SAXS.png}
-		\caption{}\label{fig:SAXS}
-	\end{subfigure}
-	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
-	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
-	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
+%		\includegraphics[width=\linewidth]{SAXS.png}
+%		\caption{}\label{fig:SAXS}
+%	\end{subfigure}
+%	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
+%	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
+%	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
         %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
@@
 	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
-  \end{figure}
-
-  In addition to the parallel displaced and sandwiched configurations we observed
-  that the initial distance between layers can influence the approach towards 
-  equilibrium.
-  \begin{itemize}
-  	\item Our choice of distance between layers results in long-term stability of 
-	qualitatively different configurations suggesting that we have found more than
-        one metastable free energy basin.
+%  \end{figure}
+
+  The $z$-direction correlation functions show that layers in our model prefer
+  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
+  with layers stacked 4.0 $\nm$ apart and to our surprise, we observed
+  long-term stability of a qualitatively different configurations suggesting
+  that we have found more than one metastable free energy basin.
+  %that the initial distance between layers can influence the approach towards 
+  %equilibrium.
+  \begin{itemize}
   	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
@@
         \item We will refer to this large set of configurations, with an open pore, as 
-        Basin OP (open pore) (Figure~\ref{fig:abasin}).
+        the OP Basin (open pore) (Figure~\ref{fig:abasin}).
 	\item Simulations of systems built with layers stacked greater than 4 
@@
 	hydrophilic regions.
-	\item This will be called Basin CP (closed pore) (Figure~\ref{fig:bbasin}).
+	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:bbasin}).
 	\item This LLC membrane may exist in at least two metastable states.
@@
 
-  We created systems using three 
-  distinct initial configurations and examined their structure by simulating 
-  X-ray diffraction patterns produced from equilibrated MD trajectories.
-  \begin{itemize}
-  	\item Systems were built in both the parallel displaced and sandwiched 
+  We answer question (3) by simulating X-ray diffraction patterns produced from
+  equilibrated MD trajectories. We leave open the possibility that the 
+  experimental structure might be reminiscent of the parallel displaced or sandwiched
+  configurations in the OP or CP basins.
+  %We created systems using three distinct initial configurations and examined
+  %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
+  \begin{itemize}
+  	\item OP Basin systems were built in both the parallel displaced and sandwiched 
 	configurations with an intial layer spacing of 3.7 \angstrom~.
@@
 	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
-	\item For ease of reference, the third system will be referred to as Basin D (disordered). 
 	\item The three systems were equilibrated according to our procedure with
@@
   % Also maybe don't talk about question 4 until after this
-  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  patterns shows the most consistency with the offset configuration in the OP basin.
+
+  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
+  %patterns shows the most consistency with the offset configuration in the OP basin.
+
+  Simulated diffraction of the disordered pore structure in the both the sandwiched
+  and parallel displaced configurations does not match the experimental pattern.
   \begin{itemize}
@@
 	R-$\pi$ and R-spots are not present. 
-        \item Simulated XRD of the sandwiched configuration contains all features 
-        except for R-helix.
-        \item Most notably, R-spots appears in the expected location, which suggests 
-        that there is something intrinsic to the sandwiched packing that gives rise 
-        to such features.
-
-	\item The equilibrated parallel displaced structure exhibits R-alkanes and
-	R-pores in the expected locations. 
         \item Due to low resolution, making out the individual spots of R-pores is
@@
         information can be extracted by measuring the pore spacing as described earlier.
+        %BJC: ^^^This can be more concise 
+        \item Although the structure's diffraction pattern is very different from
+        experiment, its long-term stability suggests that the structure is realistic.
+	We will explore this further when addressing (4). 
+  \end{itemize}
+
+  Simulated XRD of the sandwiched configuration contains all experimental features
+  except for R-helix.
+  \begin{itemize}
+        \item R-alkanes and R-pores appear in the expected locations.
         \item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
-	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
+        in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as % update distance if needed
         opposed to 3.7 \angstrom~.
-	\item R-helix and R-spots are also both missing.
-	\item The line which intersected both of these features in the restrained 
-	simulations faded upon equilibration which suggests that monomers in the 
-	parallel-displaced configuration may not give rise to the experimental WAXS 
-	pattern seen.
-	\item Simulated XRD of the sandwiched configuration contains all features 
-	except for R-helix.
         \item Most notably, R-spots appears in the expected location, which suggests 
-	that there is something intrinsic to the sandwiched packing that gives rise 
+        that there is something intrinsic to closer packing that gives rise 
         to such features. 
+  \end{itemize}
+
+  The parallel displaced configuration results in a simulated XRD pattern with 
+  the closest match to experiment. 
+  \begin{itemize}
+	\item It produces the only pattern that exhibits all major reflections
+	\item R-alkanes, R-pores and R-$\pi$ appear as they do in the sandwiched configuration. 
+	\item R-spots appears, however with a lower intensity relative to R-alkanes
+        when compared to the sandwiched configuration.
+        \item R-helix appears apparently due to the parallel displaced aromatic rings
+        %BJC: Maybe a figure to explain why this happens
   \end{itemize}
@@
 
-  The spots that appear in the simulated XRD pattern of OP basin
+  The spots that appear in the simulated XRD pattern of the OP basin
   conformations are a result of the way alkane tails pack together.
@@
 	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
-	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.i
+	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
 	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely

### 2017-09-26 Ben_Manuscripts/Paper1/figures/tail_packing.tex
More organization

--- 2017-09-25 Ben_Manuscripts/Paper1/Outline.tex
@@
 \usepackage{graphicx}
-\usepackage{wrapfig}
 \usepackage{subcaption}
 \usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\usepackage{cleveref}
-\usepackage{booktabs}
 \usepackage{gensymb}
-\usepackage{float}
-\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
+
 \begin{document}
-  \bibliographystyle{ieeetr}
-  \graphicspath{{./figures/}}
-  \maketitle
-  \section*{Introduction}
-
-  Nanostructured membrane materials have become increasingly popular for 
-  aqueous separations applications such as desalination and biorefinement
-  because they offer the ability to control membrane architecture at the
-  atomic scale allowing the design of solute-specific separation membranes. \cite{humplik_nanostructured_2011}
-  \begin{itemize}
-    \item Most membrane-based aqueous separations of small molecules can 
-    be achieved using reverse osmosis (RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}
-  \end{itemize}
-
-  While RO and NF have seen many advances in the past few decades, they 
-  are far from perfect separation technologies.
-  \begin{itemize}
-    \item \textit{RO membranes}
-    \item Inconsistent performance : Current state-of-the-art RO membranes are unstructured with
-    tortuous and polydisperse diffusion pathways which leads to 
-    inconsistent performance \cite{song_nano_2011}
-    \item High energy requirements : Necessarily high feed pressures 
-    drive up energy requirements which strains developing regions and
-    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
-    \item Separation based on differences in solubility and diffusivity:
-    Moreover, designing RO membranes to achieve targeted separations of 
-    specific solutes is nearly impossible because various solutes dissolve
-    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
-    \item At best, one can exploit these differences to create a functional
-    selective barrier.
-    \item \textit{NF membranes}
-    \item NF was introduced as an intermediate between RO and ultrafiltration,
-    having the ability to separate organic matter and salts on the order of 
-    one nanometer in size.
-    \item Larger and well-defined pores drive down energy requirements while
-    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
-    \item NF is often used as a precursor to reverse osmosis
-    \item Unfortunately, NF membranes, like RO, possess a pore size 
-    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
-  \end{itemize}
-
-  Nanostructured membranes can bypass many of the performance issues which
-  plague traditional NF and RO membranes.
-  \begin{itemize}
-    \item Tune size and functionality of building blocks to control pore
-    size and shape: One can accomplish targeted separations with high 
-    selectivity by tuning shape, size and functionality of the molecular
-    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
-    \item As a result, solute rejecting pores can have their sizes tuned
-    uniformly, resulting in strict size cut-offs.
-    \item Entirely different mechanisms may govern transport in a given
-    nanostructured material which can inspire novel separation techniques.
-  \end{itemize}
-
-  Development of nanostructured materials has been limited by the ability
-  to synthesize and scale various fundamentally sound technologies.
-  \begin{itemize}
-    \item Graphene sheets are atomically thick which results in excellent
-    permeability but defects during manufacturing severely impact 
-    selectivity. \cite{cohen-tanugi_multilayer_2016}
-    \item Molecular dynamics simulations of carbon nanotubes show
-    promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
-    unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
-    \item Zeolites have sub-nm pores with a narrow pore size 
-    distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
-    however, experimental rejection was low and attributed to interstitial
-    defects formed during membrane synthesis \cite{li_desalination_2004}
-    \item There is a need for a scalable nanostructured membrane
-  \end{itemize}
-
-  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
-  aqueous separation applications. 
-  \begin{itemize}
-    \item LLCs share the characteristic ability of nanostructured membrane
-    materials to create highly ordered structures with the added benefits
-    of low cost and synthetic techniques feasible for 
-    large scale production \cite{feng_scalable_2014}
-    \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-    phase. The presence of small amounts of water results in the H\textsubscript{II} 
-    phase.
-    \item In both cases, monomers assemble into mesophases made of hexagonally
-    packed, uniform size, cylinders with hydrophilic groups oriented inward
-    towards the pore center and hydrophobic groups facing outward.
-    \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
-    the monomer named Na-GA3C11 has been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
-    zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
-    \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
-    aligned, resulting in a low flux membrane, slowing research in the field.
-    \item In 2014, Feng et al. showed that the mesophases could be aligned 
-    using a magnetic field with subsequent crosslinking to lock the structure
-    in place \cite{feng_scalable_2014}
-    \item In 2016, Feng et al. showed that the same result could be obtained 
-    using a technique termed soft confinement \cite{feng_thin_2016}.
-    \item Following this breakthrough, research into LLC membranes has been
-    reinvigorated
-  \end{itemize}
-
-  A molecular level understanding of LLC membrane structure, enabled by molecular
-  dynamics simulations, will provide guidelines to reduce the large chemical space
-  available to design monomers for creation of separation-specific membranes.
-  \begin{itemize}
-%     \item LLCs are versatile and controllable with a \textbf{large chemical design
-%     space} available for membrane design  %BJC: redundant
-    \item Over the past 20 years, HII phase LLC membrane studies have been limited primarily
-    to Na-GA3C11 with some characterization done after minor structural modifications
-    \cite{resel_structural_2000}.
-    \item Rejection studies show that this membrane can not perform separations of
-    solutes less than 1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
-    \item  We do not yet understand how to reduce the effective pore size or 
-    how to tune the chemical environment in the nanopores for effective water
-    desalination or small organic molecule separations.
-    \item It will be challenging to efficiently narrow down the large design space in 
-    a laboratory setting without a robust model.
-    \item The only source of predictive modeling has been macroscopic models 
-    which likely do not adequately describe transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
-    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
-    \item Choice of counterion may influence the establishment of a Donnan potential
-    affecting the degree to which the membrane can exclude charged species.
-    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
-    structure which will be crucial to understanding the role of monomer structure in 
-    membrane design.
-    \item Molecular dynamics will have the required level of detail
-  \end{itemize}
-
-  Our approach to constructing a general model will follow the development of a
-  model of a specific LLC membrane with sufficient experimental characterization. %BJC: ample too much?
-    \begin{itemize}
-	    \item We have chosen to focus on assemblies formed by Na-GA3C11
-	    \item We have also narrowed our scope to the development of 
-	    a model of the Col\textsubscript{h} phase membrane.
-	    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-	    phase is a simpler starting point, due to the absence of water, and has
-	    equivalent experimental structural data.
-	    \item Despite having structural data, there is still information which 
-	    experiment cannot definitively answer.
-    \end{itemize}
-
-%BJC: the following just seems like filler now that I've reorganized
-%   A clear picture of the nanoscopic LLC membrane structure, gained by building 
-%   a molecular model will provide evidence to answer existing and newly proposed
-%   questions.
-%     \begin{itemize}
-%     \item Despite having structural data, there is still information which 
-%     experiment cannot definitively answer
-%     \end{itemize}
-
-%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
-%BJC: I moved the logic for choice of monomer to system to model to a separate paragraph (above this).
-I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).
-
-%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems.
-That is the main rationale, and it should be made clear fairly early in the introduction.
-Very important to make your story absolutely as clear as possible.
-%BJC: I moved and edited a paragraph that was originally later on to be 2 above this one.
-I think it does a better job addressing points 2 and 3.
-And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)
-
-  Despite having structural data, there is still information which 
-  experiment cannot definitively answer. There are several key 
-  questions that we intend to answer which will be laid out and numbered
-  in subsequent paragraphs.
-
-  (1) Do monomers partition into and persist as defined monomer layers?
-  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
-  thought to be composed of monomer layers stacked on top of each other. 
-  \begin{itemize}
-  	\item Their existence is supported by experimental evidence of strong 
-	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
-	membrane plane.
-	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
-	leaves no description of what is happening in monomer tail region
-	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
-	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
-  \end{itemize}
-
-  (2) If layers do exist, how many monomers constitute a single layer?
-  There has been no definitive answer to the question in literature.
-  \begin{itemize}
-    \item A simple molecular simulation study of a similar molecule suggested
-    that there are 4 monomers in each layer. Their estimation is based on a
-    simulated system containing only 16 total monomers which likely does not sufficiently
-    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
-    \item A separate calculation based on the volume of the liquid crystal monomers proposes
-    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-    \item A molecular model orders of magnitude larger than any other reported atomistic 
-    liquid crystal membrane simulations has the best chance of directly answering this question.
-  \end{itemize}
-
-   (3) How do monomers in each layer position themselves with respect to surrounding 
-   layers?
-%     Even if we knew the number of monomers in each layer, we still would not know how 
-%     monomers in each layer are positioned with respect to other layers. 
-   \begin{itemize}
-      \item A driving force of self assembly in this system is thought to be $\pi$-$\pi$
-      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
-      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
-      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
-      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
-      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
-      attraction which favors the parallel displaced configuration in all cases
-      except where the substitutions are extremely electron withdrawing
-      \cite{waller_hybrid_2006,ringer_effect_2006}.
-      \item We can use simulated X-ray diffration patterns to compare the two 
-      stacking configurations. 
-   \end{itemize}
-
-%     \item While we might be able to provide answers to these questions using a 
-%     molecular model, there remains the possibility that there is more than one 
-%     metastable state associated with a given LLC system.
-
-  (4) Can the system exist in other metastable states or phases that are not
-  accessed during experiments?
-  There remains the possibility that there is more than one metastable state 
-  associated with a given LLC system.
-  \begin{itemize}
-    \item Simulating a membrane atomistically will require many atoms which further
-    limits the timescales acessible with MD
-    \item It is reasonable to expect that we will generate configurations which 
-    are kinetically trapped in a metastable free energy basin
-    \item We must be able to identify which state is produced experimentally and 
-    why others are not.
-  \end{itemize}
-
-  Once we have addressed all of the above questions, we must show that the 
-  developed molecular model is consistent with physical observations so that we
-  can rely on conclusions drawn about structural features characteristic of 
-  the system.
-  \begin{itemize}
-    \item In this study, we build a significantly more realistic atomistic model of LLC membranes 
-    than has ever previously been done, and explore what new structural information can be gained
-    and what structure hypotheses are supported by this model.
-    \item We validate the model using as much experimental information as possible.
-    \item We are most interested in reproducing the conclusions about structure
-    which have been made from X-ray diffraction (XRD) experiments and in matching ionic
-    conductivity measurements~\cite{feng_thin_2016}.
-    \begin{itemize}
-	    \item We have compared simulated X-ray diffraction patterns to experiment in 
-	    order to match major features present in the 2D patterns.
-	    \item We calculated ionic conductivity using two agreeing methods.
-	    \item We examined the the influence of crosslinking on membrane structure.
-    \end{itemize}
-    \item The structure-building approach and analysis used in this paper can be readily extended
-    to the H\textsubscript{II} phase and other similar LC systems.
-  \end{itemize}
-
-  \section*{Methods}
-
-  Liquid crystal monomers were parameterized using the Generalized AMBER Forcefield
-  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
-  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
-  assigned using tools from Openeye Scientific Software. All molecular dynamics 
-  simulations were run using the latest version of Gromacs 2016. 
-  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-
-  An ensemble of characteristic, low-energy vacuum monomer configurations
-  were constructed by applying a simulated annealing process to a
-  parameterized monomer.
-  \begin{itemize}
-    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
-    \item A low energy configuration was randomly pulled from the trajectory
-    and charges were reassigned using the am1bccsym method of molcharge
-    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
-    \item Using the new charges, the monomer system was annealed again and monomer
-    configurations were pulled from the trajectory to be used for full
-    system construction (Figure~\ref{fig:python}a).
-  \end{itemize}
-
-  The timescale for self assembly of monomers into the hexagonal phase is
-  unknown and likely outside of a reasonable length for an atomistic
-  simulation, calling for a more efficient way to build the system. 
-  \begin{itemize}
-    \item Previous work has shown a coarse grain model self assemble into
-    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
-    \item We attempted atomistic self-assembly by packing monomers into a box 
-    using Packmol \cite{martinez_packmol:_2009}.
-    \item Simulations of greater than 100 ns show no indicators of progress 
-    towards an ordered system.
-    \item To bypass the slow self-assembly process, python scripts are used
-    to assemble monomers into a structure close to one of a number of 
-    hypothesized equilibrium configurations (Figure~\ref{fig:python}).
-   \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
-	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
-		configuration. (b) Monomers are rotated and assembled into layers with 
-		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
-		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
-  \end{figure}
-
-  A typical simulation volume contains four pores in a monoclinic unit cell,
-  the smallest unit cell that maintains hexagonal symmetry when extended 
-  periodically.
-  \begin{itemize}
-    \item Each pore is made of twenty stacked monomer layers with periodic 
-    continuity in the z direction, avoiding any edge effects and creating an 
-    infinite length pore ideal for studying transport.
-    \item A small number of layers is preferred in order to reduce computational
-    cost and to allow us to look at longer timescales.
-    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
-    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
-    This point will be explained in more detail later.
-    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
-    %BJC: so refer to supporting info here?
-Then put plots of diffraction data with different sized system there.
-I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense.
-And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
-    \item We chose initial guesses for the remaining structural parameters based on
-    experimental data and treated them as variables during model development.
-  \end{itemize}
-
-  We used experimental wide angle X-ray scattering (WAXS) data (produced as described 
-  in~\cite{feng_scalable_2014}) and small angle X-ray scattering (SAXS) data from~\cite{feng_thin_2016}
-  to inform some of our initial guess choices (Figure~\ref{fig:SWAXS}). We rely primarily
-  on the 2D WAXS data since it encodes all structural details down to the sub-nm scale.
-  \begin{itemize}
-        \item There are five major features of interest present in the 2D experimental
-        pattern shown in Figure~\ref{fig:WAXS}.
-        \item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
-        corresponding to a real spacing of 3.7 \angstrom~. The reflection is
-        attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-        perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
-        reflection will be referred to as R-$\pi$.
-        \item A weak intensity line is located at exactly half the $q_z$ value of
-        R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a
-        real space periodic spacing of 7.4 \angstrom~. This reflection has been
-        interpreted  as 2\textsubscript{1} helical ordering of aromatic rings
-        along the z axis meaning if the positions of the aromatic rings can
-        be traced by a helix, then for each turn in the helix, there should be
-        two aromatic rings. For this reason it will be referred to as R-helix.
-        \item A third major reflection is marked by a low intensity ring located
-        at r = 1.4 \angstrom$^-1$. The real space separation
-        corresponds to 4.5 \angstrom~ which is characteristic of the average
-        spacing between packed alkane chains. This reflection will be called R-alkanes.
-        \item Within R-alkanes, are four spots of higher intensity which
-        will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
-        in their respective quadrants. In many liquid crystal systems this can be
-        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
-        \item The first corresponds to the spacing and symmetry of
-        the d\textsubscript{100} plane which can be related to the distance between
-        pores. The feature, which will be called R-pores, is characterized by dots
-        along $q_z$ = 0. The spacing between dots is indicative of the hexagonal
-        symmetry of the packed pores. The same information is obtained using a SAXS
-        setup. By radially integrating the 2D data one gets a 1D curve which is 
-        shown in Figure~\ref{fig:SAXS}.  % BJC: I also have 2D SAXS data
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[t]{0.43\linewidth}
-                \centering
-        %       \vspace{12mm}
-                \includegraphics[width=\linewidth]{SAXS.png}
-                \caption{}\label{fig:SAXS}
-        \end{subfigure}
-        \begin{subfigure}[t]{0.47\linewidth}
-                \centering
-                \raisebox{.2\textwidth}{%
-                \includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-                }
-                \caption{}\label{fig:WAXS}
-        \end{subfigure}
-        \caption{(a) 2D wide angle X-ray scattering gives details about repeating
-        features less than 1 nanometer apart. (b) 1D small angle X-ray scattering
-        indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
-  \end{figure}
-
-%  We chose an initial layer spacing based on experimental 2D WAXS data.
-%  \begin{itemize}  
-%    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
-%    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
-%    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
-%    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-%    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
-%    spacings greater than 4 \angstrom~.
-%  \end{itemize}
-
-  We chose an initial layer spacing based on R-$\pi$.
-  \begin{itemize}  
-    \item Each monomer was rotated so the plane of the aromatic ring on the
-    head groups would be parallel to the xy plane.
-    \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
-    apart in the z-direction.
-    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
-    spacings greater than 4 \angstrom~.
-  \end{itemize}
-
-  We placed pores at a chosen initial spacing based on R-pores, then allowed
-  the system to settle into its preferred spacing. 
-  \begin{itemize}
-    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
-    %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
-    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
-    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
-    resulting from a tightly packed initial configuration.
-    \item To calculate the equilibrated pore spacing, we measured the distance between pore
-    centers.
-    \item Pore centers were located by averaging the coordinates of sodium ions in their 
-    respective pores.
-    \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
-    %BJC: Do bootstrapping details go in supplemental?
-    	% Supplemental vvvv
-	\begin{itemize}
-    	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
-    	sampling from the original trajectory
-    	\item Each pore spacing has its own trajectory with its own average value
-    	\item The average value of each pore spacing is averaged to get the overall
-    	average pore spacing. 
-    	\item The standard deviation of average values is reported as the uncertainty in pore spacing
-    	% BJC: The following will go in supplemental
-        \item We are interested in 5 pore-to-pore distances which should all be equal in 
-        a perfect hexagonal array. Only 4 are independent  
-        % Supplemental ^^^^
-	\end{itemize}
-  \end{itemize}
-
-  %MRS: pore radius is a different category isn't it? Is this an input piece of data?
-  % should be put in a different category.
-  %BJC: Well I still have to initially place the monomers some distance away from the pore
-  % centers. That distance is informed by the experimental evidence.
-
-  We based the pore radii of our initial configuration on past TEM and size exclusion 
-  rejection data
-  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
-  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
-  of pore radius in the initial configuration.
-  \begin{itemize}
-    \item Experimental evidence suggests uniform pores with radii of 0.6 nm 
-    \item Comparing a geometric measurement of pore size derived from an atomistic model,
-    to a less precise, experimentally derived pore size estimate, will give ambiguous results.
-    \item What is meant by pore radius will not be clear until we establish a clear picture
-    of the nanoscopic pore environment.
-    \item When constructing pores, we chose the carboxylate carbon from the monomer
-    head group as a reference atom, and placed it a distance r from the pore center,
-    where r is the pore radius. (See Supplemental Information) %BJC: figure making that clear
-    \item We will not make direct comparisons of pore radius between our model 
-    and experiment to avoid the ambiguity, however, we do define a pore radius based 
-    for our own purposes.
-    \item To measure the pore radius in our model we calculate the distance between 
-    the center of mass of each aromatic ring and the center of mass of all aromatic rings
-    in their respective pores.
-  \end{itemize}
-
-  The relative interlayer orientation was chosen based on clues from 
-  diffraction data as well as the various known stacking modes of benzene 
-  and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
-  ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
-  \begin{itemize}
-    \item The T-shaped configuration was ruled out based on the inconsistency of
-    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
-    \item The system's preference towards the sandwiched vs. parallel displaced 
-    stacking modes will be explored.
-    \item Both have reported stacking distances near 3.7 \angstrom
-    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
-    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
-    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.
-This is what we fix, this is what we leave as a variable.
-The analysis probably belongs later.
-    %BJC: Yeah, I will leave the rest for discussion
-%     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
-%     suggests entropic differences based on the way the tails are able to pack.
-%     \item In the sandwiched configuration, all tails start out directly on top
-%     of each other which may prevent closely stacked benzene rings.
-%     \item In the offset configuration, the tails are placed in between each other 
-%     which may allow layers to come together in a compact way.
-%     \item This difference may explain, in part, which stacking mode is more favorable.
-  \end{itemize}
-
-  % This can be cut down if C and D prove to be no help. 
-  We tested a number of equilibration schemes of increasing complexity in an effort
-  to match experiment while overcoming kinetic limitations that might trap the system 
-  in a metastable states. All start from an initial configuration generated with 
-  chosen structure variables. 
-  \begin{itemize}
-      \item Equilibration Scheme A:
-      \begin{itemize}
-          \item Steepest descent energy minimization
-          \item Short NPT simulation (~ 5 ns ) with berendsen barostat (tau-p = 1) at 300 K 
-          \item Switch to Parrinello-Rahman (tau-p = 10) and run NPT simulation for 400 - 500 ns
-          %\item Final structure strongly influenced by monomer configuration used to build 
-      \end{itemize}
-      \item Equilibration Scheme B:
-      \begin{itemize}
-          \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-          configurations while allowing monomer tails to settle.
-          \item Doing so also mitigates system dependence on initial monomer configuration.
-          \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
-          \item Every 50 ps, we reduce the force constants by the square root of its
-          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
-          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
-          slowly released until there is no more restraining potential.
-          \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-          ensemble for 400 - 500 ns in the same way as Scheme A.
-      \end{itemize}
-      \item Equilibration Scheme C:
-      \begin{itemize} 
-          \item A system equilibrated according to scheme B is cut in half so we can access
-          longer simulation timescales
-          \item The system is simulated at 335K, close to its isotropic transition temperature, for 200 ns. % BJC: not entirely sure if it needs to be an already equilibrate structure
-          \item The structure is then linearly cooled back down to 300 K over 500 ns. 
-          \item The system size is doubled back to its original size and equilibrated for 200 ns at 300 K.
-          \item Tried with and without an applied electric field.
-      \end{itemize}
-      \item Equilibration Scheme D:
-      \begin{itemize}
-          \item Even in the near dry Col\textsubscript{h} system, there exists an
-          equilibrium concentration of water.
-          \item The hydrogen bonding network formed by the water may play a role 
-          in structuring the pore.
-          \item We obtained an estimate of equilibrium pore water content by solvating
-          an initial configuration with water baths above and below the membrane. 
-	  \item We ran the solvated system according to Scheme A but for 1000 ns
-          \item Using that number we added water to the pores of an initial 
-	  configuration and equilibrated according to scheme B. 
-      \end{itemize}
-      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1
-  \end{itemize}
-
-%  An equilibration scheme with position restraints placed on aromatic rings
-  %MRS: 
-  %prevents 
-%  during early equilibration steps is required to prevent high energy repulsions .
-  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
-  %BJC: 'high energy repulsions' ?
-%  \begin{itemize}
-%    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-%    configurations while allowing monomer tails to settle.
-%    \item Doing so also mitigates system dependence on initial monomer configuration.
-%    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
-%    \item Every 50 ps, we reduce the force constants by the square root of its 
-%    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
-%    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
-%    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
-%    restraining potential.  
-%    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-%    ensemble for 400 - 500 ns.
-   %BJC: I will reference an equilibration script that can be released with the supplemental info
-   %MRS: we should release as many scripts as is feasible, can be in a github repository.
-   %BJC: Okay, once we submit, I will need to spend some time cleaning the scripts
-   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
-   %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
-%  \end{itemize}
-
-  %BJC: the following paragraph will be replaced with something that Joe writes
-  %MRS: sounds good.
-
-  % BJC: The following methodology is taken from the 2014 Feng et al. paper where
-  % WAXS is reported. The data we are using comes from the 2016 paper which 
-  % I assume used the same set up but I will need to verify this with Xunda
-  % before this gets sent out. The SAXS is the same as shown in the 2016 paper
-  % however I will likely reproduce it with matplotlib
-
-  %\Experimental wide angle X-ray scattering measurements were performed using a 
-  %Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
-  %($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
-  %calibrations of the resultant 2-D WAXS patterns were done by using a 
-  %silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
-  %patterns were integrated into 1-D plots of scattering intensity (I) versus
-  %q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
-  %2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.
-
-  Simulated X-ray diffraction patterns were generated based on atomic
-  coordinates for a direct experimental comparison.
-  \begin{itemize}
-    \item All atomic coordinates were simulated as gaussian spheres of electron
-    density corresponding to each atom's atomic number.
-    \item A three dimensional fourier transform (FT) of the array of electron 
-    density results in a three dimensional structure factor which represents
-    the unit cell in reciprocal space.
-   % \item We perform an angular average of the structure factor about the 
-    z axis to generate a 2D cross section close to what one would see 
-    experimentally.
-    \item We matched experimental 2D WAXS patterns by iterative improvement
-    of our choice of initial structure and equilibration procedure.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{}\label{fig:sandwiched}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{PD.png}
-		\caption{}\label{fig:pd}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{}\label{fig:tshaped}
-	\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwichedlayers.png}
-		\caption{}\label{fig:sandwichedlayers}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{offsetlayers.png}
-		\caption{}\label{fig:offsetlayers}
-	\end{subfigure}
-	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
-	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
-	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
-	configuration }\label{fig:stacking}
-  \end{figure}
-
-  We calculated ionic conductivity using two different methods for robustness.
-  \begin{itemize}
-    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
-    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
-    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
-    \item Sodium ion diffusion coefficients were found by calculating the slope
-    of the linear region of the mean square displacement curve as indicated by
-    the einstein relation \cite{einstein_investigations_1956}.]
-    %MRS: state how you decided which was the linear region.
-    %BJC: nothing fancy other than looking at the msd plot and determining where to
-    % start fitting. I suppose I could minimize R^2 but that seems like overkill
-    \item We looked at the MSD plot to determine where to begin and end a linear fit
-    \item Ion concentration was measured with respect to the entire unit cell. 
-    \item The second method, termed the 'Collective Diffusion' model, measures 
-    the movement of the collective variable, Q, which is defined as the amount
-    of charge transfer through the system and can be thought to represent
-    the center of charge of the system.
-    \item The conductance, $\gamma$ of the system can be calculated as:
-    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
-    achieved by multiplying by channel length and dividing by the membrane
-    cross sectional area.
-    \item $D_Q$ is the diffusion coefficient of the collective variable Q. It can
-    be calculated using the einstein relation.
-    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
-  \end{itemize}
-
-  Using an equilibrated structure, a crosslinking procedure was performed
-  in order to better parallel synthetic procedures. 
-  \begin{itemize}
-    \item The purpose of crosslinking is to maintain macroscopic alignment of 
-    the crystalline domains, ensuring aligned, hexagonally packed pores.
-    \item For that reason, we are not concerned with replicating the kinetics 
-    of the reaction, but instead emphasize the consistency of the final structure
-    with experimental structural data.
-    \item The algorithm was developed based on the known reaction mechanism.
-    \item Crosslinking of this system is a free radical polymerization (FRP)
-    taking place between terminal vinyl groups present on each of the three
-    monomer tails.
-    \item FRPs require an initiator which bonds to the system, meaning new atoms
-    were introduced into the system.
-    \item For simplicity, the initiator was simulated as hydrogen and made present 
-    in the simulation by including them in all possible bonding positions as dummy atoms.
-    \item The crosslinking procedure is carried out iteratively.
-    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
-    \item The topology is updated with new bonds and dummy hydrogen atoms are 
-    changed to appropriate hydrogen types. 
-    \item Head-to-tail addition was the only propagation mode considered due to 
-    its dominance the real system.
-    \item Direction of attack was not considered because the resultant mixture 
-    is racemic.
-    %BJC: The following items belongs in results/discussion
-    %MRS: probably. 
-    \item The resulting crosslinked structure has an even distribution of
-    crosslinks between monomer tails of the same monomer, monomers stacked on
-    top of each other and monomers in other pores, including across periodic
-    boundaries.
-    \item The pore spacing shrinks by $\approx$ 1 \angstrom~ and stays 
-    constant under a range of simulation conditions.
-  \end{itemize}
-
-  \section*{Results and Discussion}
-
-  \subsection*{Determination of Nanoscopic Structural Details}
-
-  %In order to construct an initial configuration which gives reliable 
-  %trends, we need to understand the composition of layers, how far apart
-  %to stack the layers, and how to orient them with respect to each other.
-  %\begin{itemize}
-  %	\item To verify our choices for each parameter, we compare our calculations
-  %	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
-  %	scattering (WAXS), and ionic conductivity measurements.
-  %\end{itemize}
-
-  We will now address the questions raised in the introduction in the order
-  that they were asked.  %BJC: I dont like this
-
-  To answer (1), we verified that the system stays partitioned into layers by
-  plotting the pair correlation function calculated between aromatic rings along
-  the length of the pores (Fig~\ref{fig:zdf}).
-  % BJC: add how this calculation is done to methods section (put where I talk about
-  % choosing distance between layers
-  \begin{itemize}
-	\item Period of fluctuation (layer spacing)
-        \item Magnitude of fluctuations
-	\item Comment on difference between offset/layered, number of monomers per layer
-  \end{itemize}
-
-  To discern the composition of the monomer layers, addressing (2), we ran 
-  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
-  \begin{itemize}
-  	\item Both the sandwiched and parallel displaced configurations were tested.
-	\item All systems are stable after 50 ns of simulation.  % BJC: edited this for clarity
-        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
-        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
-        %MRS: remind people where the uncertainty comes from.
-	%BJC: It looks like the 7 and 8 monomer systems were only run for 50 ns.
-The 4 monomer system was run for 200 ns.
-5 and 6 have a lot of data.
-7 and 8 flattened pretty quickly, so at the time I figured it wasn't worth continuing.
-But I'll extend them just to be thorough.
-	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
-	Systems built with 5 monomers in each layer equilibrate to a pore spacing
-	that is most consistent with the experimental value of 4.12 nm derived from
-	SAXS measurements (Figure~\ref{fig:SAXS}).
-	\item The remainder of this discussion will focus on the analysis of systems
-	built with 5 monomers per layer. 
-  \end{itemize}
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  		   & \multicolumn{2}{c}{Starting Configuration} \\
-  \hline
-  Monomers per layer & Sandwiched & Parallel Displaced \\
-  \midrule
-  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
-  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
-  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
-  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
-  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
-  \bottomrule
-  \end{tabular}
-  \caption{The pore spacing 
-  %MRS added
-  (given in \angstrom~)
-  of the model increases as number of monomers
-  in each layer increases. The pore spacing of a system starting in the 
-  sandwiched configuration is systematically lower than that started in an 
-  offset configuration. Systems built with 5 monomers per layer in a parallel
-  displaced configuration result in a pore spacing closest 
-  %MRS: clarified.
-  %to experimental data
-  to the experimental 4.12 \angstrom~}\label{table:p2p} 
-  \end{table}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5layered.png}
-		\caption{}\label{fig:zdf_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5offset.png}
-		\caption{}\label{fig:zdf_offset}
-	\end{subfigure}
-	\caption{Pair distribution functions of aromatic carbons for the
-	(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, 
-	parallel displaced configurations. 
-        %MRS: added some info.
-        Clear periodic maxima in the $z$ probability density indicate
-        % Spikes in the distribution mark
-	distinct layers. The magnitude of the spikes with respect to the 
-	average suggest that the 5 monomer per layer, sandwiched configuration
-	possesses a higher degree of layer partitioning.}\label{fig:zdf}
-  \end{figure}
-
-  To answer question (3) we require high resolution experimental evidence which we 
-  can match to our simulations. Experimental WAXS measurements encode all structural
-  details and we would like to match them as well as possible. 
-  %MRS: also encodes the pore spacing
-  %BJC: got rid of 'remaining' in 'remaining structural details'
-  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
-  \begin{itemize}
-  	\item There are five major features present in the 2D experimental 
-	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
-	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
-	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
-	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-	perpendicular to the membrane plane, or z-axis. For simplicity, this 
-	reflection will be referred to as R-$\pi$.
-        %MRS: why R in R-pi? for reflection?
-	%BJC: yes, R = reflection
-	\item A weak intensity line is located at exactly half the $q_z$ value of
-	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
-	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
-	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
-	along the z axis meaning if the positions of the aromatic rings can
-	be traced by a helix, then for each turn in the helix, there should be
-	two aromatic rings. For this reason it will be referred to as R-helix.
-	\item A third major reflection is marked by a low intensity ring located
-	at r = 1.4 \angstrom$^-1$. The real space separation 
-	corresponds to 4.5 \angstrom~ which is characteristic of the average 
-	spacing between packed alkane chains. This reflection will be called R-alkanes.
-	\item Within R-alkanes, are four spots of higher intensity which 
-	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
-	in their respective quadrants. In many liquid crystal systems this can be
-	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
-	\item The final major reflections correspond to the spacing and symmetry of 
-	the d\textsubscript{100} plane which can be related to the distance between
-	pores. The feature, which will be called R-pores, is characterized by dots 
-	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
-	symmetry of the packed pores. It is easiest to interpret the data by 
-	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}[t]{0.47\linewidth}
-		\centering
-		\raisebox{.2\textwidth}{%
-		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-		}
-		\caption{}\label{fig:WAXS}
-	\end{subfigure}
-	\begin{subfigure}[t]{0.43\linewidth}
-		\centering
-	%	\vspace{12mm}
-		\includegraphics[width=\linewidth]{SAXS.png}
-		\caption{}\label{fig:SAXS}
-	\end{subfigure}
-	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
-	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
-	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
-        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
-	%BJC: 1D is from a Yale paper. I'm going to remake the figure from the raw data but will reference that
-	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
-  \end{figure}
-
-  In addition to the parallel displaced and sandwiched configurations we observed
-  that the initial distance between layers can influence the approach towards 
-  equilibrium.
-  \begin{itemize}
-  	\item Our choice of distance between layers results in long-term stability of 
-	qualitatively different configurations suggesting that we have found more than
-        one metastable free energy basin.
-  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
-        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
-	structure.
-        \item We will refer to this large set of configurations, with an open pore, as 
-        Basin OP (open pore) (Figure~\ref{fig:abasin}).
-	\item Simulations of systems built with layers stacked greater than 4 
-	\angstrom~ apart results in a pore structure characterized by high radial 
-	disorder, while still maintaining partitioning between hydrophobic and 
-	hydrophilic regions.
-	\item This will be called Basin CP (closed pore) (Figure~\ref{fig:bbasin}).
-	\item This LLC membrane may exist in at least two metastable states.
-	\item The distinct difference in pore structure exhibited by each phase will 
-	likely lead to different transport mechanisms.
-	\item Because the pore structure will vary between each Basin, understanding 
-	which phase exists experimentally is necessary in order to ensure we are 
-	studying the system which actually dominates.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:abasin}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:bbasin}
-        \end{subfigure}
-	\caption{From a qualitative standpoint, Basin A (a) is characterized by a
-	hollow cylindrical pore while pores in Basin B (b) are characterized by a
-	higher degree of radial disorder}\label{fig:basins}
-  \end{figure}
-
-  % BJC: This paragraph needs to change since, upon inspection, it appears that the 
-  % offset configuration is correct. So it needs to shine a more positive light on offset
-  % BJC: I think it can be deleted
-  %We varied the initial relative interlayer orientation between sandwiched and 
-  %parallel-displaced based on our knowledge of the stability of the two
-  %pi-stacking modes.
-  %\begin{itemize}
-  %	\item We generated simulated X-ray diffraction patterns using simulation 
-  %      trajectories from the highly restrained initial configurations created during 
-  %	equilibration
-  %	\item The simulated patterns establish a difference between the two stacking 
-  %	modes (Figure~\ref{fig:XRDrestrained}).
-  %	\item In each pattern, R-alkanes is present at a distance of $\approx
-  %	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
-  %	\item R-$\pi$ is also present in each pattern, although it appears to 
-  %	intersect R-alkanes because the spacing between aromatic rings is 
-  %	similar to the alkane chain packing.
-  %     %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
-  %	%BJC: okay added some more specific language
-  %	\item The difference in aromatic ring spacing between experiment and
-  %	simulation is likely a result of the inability of GAFF to properly handle
-  %	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
-  %	\item The sandwiched configuration shows R-spots in the expected location.
-  %	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
-  %	\item The parallel displaced configuration contains two lines of high 
-  %	intensity with maximum intensity occurring where they intersect the alkane
-  %	chain region due to constructive interference between the two features.
-  %	\item The lines are located where one would expect to see R-helix and, 
-  %	perhaps coincidentally, the intersection with R-alkanes occurs where one 
-  %	would expect to see R-spots.
-	%BJC: might save the following sentence for equilibrium trajectories
-  %	\item As the simulation is progressed, the full line begins to fade 
-  %	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
-  %	where R-helix exists.
-  %\end{itemize}
-
-  %\begin{figure}[!ht]
-  %	\centering
-  %	\begin{subfigure}{0.475\textwidth}
-  %		\hspace{-1.2cm}
-  %		\centering
-  %		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
-  %		\caption{}\label{fig:rzplayeredrestrained}
-  %	\end{subfigure}
-  %	\begin{subfigure}{0.475\textwidth}
-  %		\hspace{-1.2cm}
-  %		\centering
-  %		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
-  %		\caption{}\label{fig:rzoffsetrestrained}
-  %	\end{subfigure}
-  %	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
-  %	with restraints placed on aromatic carbons shows all major features
-  %	present in experimental WAXS. Near solid lines at constant z are a result of 
-  %	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
-  %	restrained parallel displaced configuration may also contain all
-  %	major experimental WAXS features. One can argue that R-spots is not present
-  %	but it is difficult to distinguish because of its intersection with the solid
-  %	R-helix line. 
-        %MRS: Longer simulations are necessary to determine which structure
-	% is the best match to experiment
-        %MRS: we probably want to avoid saying this (above) if we can.
-%}\label{fig:XRDrestrained}
-%  \end{figure}
-
-  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.
-Something to think about.
-  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
-  %MRS: make sure the figures are comparable.
-Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
-
-  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  %patterns produced from equilibrated MD trajectories shows the most consistency
-  %with the offset configuration in the OP basin.
-
-  We created systems using three 
-  distinct initial configurations and examined their structure by simulating 
-  X-ray diffraction patterns produced from equilibrated MD trajectories.
-  \begin{itemize}
-  	\item Systems were built in both the parallel displaced and sandwiched 
-	configurations with an intial layer spacing of 3.7 \angstrom~.
-	\item A third system was created by stacking layers in the sandwiched 
-	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
-	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
-	\item For ease of reference, the third system will be referred to as Basin D (disordered). 
-	\item The three systems were equilibrated according to our procedure with
-	NPT simulations of greater than 400 ns.
-	\item Simulated diffration patterns were generated using portions of the
-	trajectory after equilibration.  
-	\item We assume the simulation has equilibrated when the distance between 
-	pores and the membrane thickness stopped changing.
-	\item Simulated diffraction patterns for all three structures are shown in 
-	Figure ~\ref{fig:XRDsim}. 
-  \end{itemize}
-
-  % Three paragraphs instead here? Talk about disordered, parallel displaced and 
-  % layered separately? Try it. 
-  % Talk about disordered last so it leads in to 
-  % Also maybe don't talk about question 4 until after this
-  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  patterns shows the most consistency with the offset configuration in the OP basin.
-  \begin{itemize}
-        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
-	R-$\pi$ and R-spots are not present. 
-        \item Simulated XRD of the sandwiched configuration contains all features 
-        except for R-helix.
-        \item Most notably, R-spots appears in the expected location, which suggests 
-        that there is something intrinsic to the sandwiched packing that gives rise 
-        to such features.
-
-	\item The equilibrated parallel displaced structure exhibits R-alkanes and
-	R-pores in the expected locations. 
-	\item Due to low resolution, making out the individual spots of R-pores is
-	challenging and can be validated with slightly better resolution upon full
-	spherical integration of the 3D structure factor. However, the same 
-	information can be extracted by measuring the pore spacing as described earlier.
-	\item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
-	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
-	opposed to 3.7 \angstrom~.
-	\item R-helix and R-spots are also both missing.
-	\item The line which intersected both of these features in the restrained 
-	simulations faded upon equilibration which suggests that monomers in the 
-	parallel-displaced configuration may not give rise to the experimental WAXS 
-	pattern seen.
-	\item Simulated XRD of the sandwiched configuration contains all features 
-	except for R-helix.
-	\item Most notably, R-spots appears in the expected location, which suggests 
-	that there is something intrinsic to the sandwiched packing that gives rise 
-	to such features. 
-  \end{itemize}
-
-% BJC: Replacement figure below this one
-%  \begin{figure}[!ht]
-%	\centering
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
-%		\caption{}\label{fig:sandwich_rzplot}
-%	\end{subfigure}
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{offset_rzplot.png}
-%		\caption{}\label{fig:offsetrzplot}
-%	\end{subfigure}
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{disorder_rzplot.png}
-%		\caption{}\label{fig:disorder_rzplot.png}
-%	\end{subfigure}
-%	\caption{(a) All major features except R-helix are present in
-%	XRD patterns resulting from an equilibrated sandwiched configuration 
-%	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
-%	(b) All major features execpt R-spots are present in XRD patterns 
-%	resulting from an equilibrated parallel displaced configuration in Basin A.
-%	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
-%	are the only major features present in XRD patterns resulting from an 
-%	equilibrated disordered phase}\label{fig:XRDsim}
- % \end{figure}
-
-  \begin{figure}[ht]
-  \begin{subfigure}{.83\linewidth}
-        \centering
-        \begin{subfigure}{0.4\linewidth}
-                \centering
-                \includegraphics[width=\linewidth, trim={2.5cm 0 4cm 2cm}, clip]{WAXS_raw.png}%
-                \caption{}~\label{fig:raw_waxs}
-        \end{subfigure}%
-        \begin{subfigure}{0.4\linewidth}
-                \centering
-                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_offset.png}
-                \caption{}~\label{fig:rz_offset}
-        \end{subfigure}
-        \begin{subfigure}{0.4\linewidth}
-                \centering
-                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_layered.png}
-                \caption{}~\label{fig:rz_layered}
-        \end{subfigure}%
-        \begin{subfigure}{0.4\linewidth}
-                \centering
-                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_disordered.png}
-                \caption{}~\label{fig:rz_disordered}
-        \end{subfigure}
-  \end{subfigure}%
-  \begin{subfigure}{0.14\linewidth}
-        \centering
-        \vspace{-1cm}
-        \includegraphics[width=\linewidth]{colorbar_jet.png}
-  \end{subfigure}
-  \caption{(a) Experimental 2D WAXS data contains 5 major reflections which we aim to match. The remaining
-  three images are diffraction patterns simulated from MD trajectories. (b) The parallel displaced
-  configuration gives rise to all reflections of interest. (c) The sandwiched configurations gives rise to a
-  pattern with all major reflections except R-helix. R-spots is strong relative to R-alkanes in comparison
-  to the parallel displaced configuration. (d) The disordered pore configuration creates a pattern with only
-  R-alkanes and R-pores in common with experiment}~\label{fig:xrd}
-  \end{figure}
-
-  The spots that appear in the simulated XRD pattern of OP basin
-  conformations are a result of the way alkane tails pack together.
-  \begin{itemize}
-  	\item Previously, the spots in the diffraction pattern had been explained 
-	as the product of tilted alkane chains.
-	\item We measured the tilt angle of the alkane chains and showed that our 
-	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
-	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.i
-	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
-        that the spots arise as a consequence of the tails. 
-	\item By removing atoms from the trajectory and simulating a diffraction 
-	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
-	\item Since the tails stay nearly flat, we plotted the centroids of the 
-	tails and measured the angle between each centroid and its nearest neighbors
-	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
-	\item The distribution of these angles is consistent with the location of 
-	the spots (Figure~\ref{fig:tail_packing}).
-	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
-	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
-	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
-	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
-        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
-        is a reconcilable difference with our simulated results.  
-  \end{itemize}
 
@@
 
-  %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
-  %MRS: we had talked a lot about interconversion (or conversion one way but not other?) but 
-  %MRS: I think things have changed since then? 
-  The disordered basin shares little in common with the ordered basin but 
-  its long term stability suggests that it can exist under some conditions.  
-  Basin B is the dominant configuration at higher temperatures.
-  \begin{itemize}
-        \item We linearly ramped the temperature of a system in Basin A
-        from 280K to 340K over 100 ns.
-        \item Visually, there is a distinct change in pore structure from one
-        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
-        Basin B (Figure~\ref{fig:340K_pore}).
-        \item The slope of all order parameters changes between 315K and 325K
-        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
-        possibility of an abrupt change in system ordering.
-        \item Our 100 ns temperature ramp was likely too fast and caused the system
-        to suffer from hysteresis.
-  \end{itemize}
-
-  We can not immediately classify Basin A and Basin B as separate phases.
-  \begin{itemize}
-	\item To prove the existence of two phases we need evidence of a
-	a first order phase transition.
-	\item A first order phase transition can be denoted by a discontinuity
-        of some order parameter in response to an external condition such as
-	temperature.
-	\item We chose three easily measurable order parameters: the distance
-	between pores, the membrane thickness and the ratio of pore radius to
-	the uncertainty in pore radius.  % BJC: these may change
-        \item The pore radius is divided by its uncertainty as a way of quantifying
-        the degree to which monomers obstruct the pore region.
-  \end{itemize}
-
-  In an attempt to mitigate hysteresis, we performed a slow, stepwise temperature ramp.
-  \begin{itemize}
-        \item Starting from a sandwiched structure equilibrated at 280K, the system
-        temperature was raised to 300K and allowed to equilibrate for 200 ns.
-        \item At the end of 200 ns, the temperature was raised 5K and equilibrated
-        again for 200 ns.
-        \item We continued raising the temperature by 5K and equilibrating for 200 ns
-        until the system was equilibrated for 200 ns at 320K.
-	\item The same process was repeated with a system equilibrated in Basin B and used
-	as a benchmark for comparison. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                % these next 2 figures are REALLY big (12-18M). Likely could reduce to near 0.5-1.0 MB without loss of 
-                % necessary resolution.  A few other figures could have resolution reduced.
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:340K_pore}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_tramp.png}
-                \caption{}\label{fig:p2p_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_tramp.png}
-
-                \caption{}\label{fig:thickness_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_tramp.png}
-                \caption{}\label{fig:order_tramp}
-        \end{subfigure}
-        \caption{(a) The open pore structure exhibited by a structure equilibrated
-        at 280K is characteristic of Basin A. (b) The closed pore structure with
-        a high degree of radial disorder exhibited when the structure in (a) is
-        heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
-        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
-        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
-        its uncertainty changes slope near 315K.}\label{fig:tramp}
-  \end{figure}
-
-  Basin A and Basin B are two configurationally metastable basins.
-  \begin{itemize}
-        \item There is litle change in disordered phase properties during the 
-        temperature ramp.
-	\item We observed smooth changes in order parameters as temperature
-        of the Basin A system was increased implying that we cannot claim the
-	existence of two phases (Figure~\ref{fig:phase_transition}).
-	\item Qualitatively, the pore structure of the Basin A system becomes
-        comparable to one characteristic of Basin B as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
-	\item The Basin A system does not converge to the same order parameter
-	values as Basin B, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
-	\item To resolve the quanitative discrepancy, we would need a slower 
-	temperature ramp
-	\item Since there are no abrupt changes in any order parameter along the 
-	trajectory, we can conclude that the two basins are not separate phases
-	\item Basin A is the closest match to what is seen experimentally
-	\item Basin B is likely an intermediate between the Col\textsubscript{h} 
-	phase and isotropic phase
-	\item Basin B is present in our simulations at lower temperatures 
-        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
-        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
-	because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
-	stabilize the system into Basin A. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-	% BJC: I'll get actual pictures of the system here. I'm not sure how 
-	% necessary this figure is though. It could go in the supplemental 
-	% information and I can reference the pictures in the previous figure
-	% since they show basically the same idea : Ordered vs. disordered pore
-	% Alternatively, I could show two diffraction patterns here from the 
-	% beginning and end temperature 
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:BasinA_280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:BasinB_340K_pore}
-        \end{subfigure}
-	\vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_layered.png}
-                \caption{}\label{fig:p2p_step}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_layered.png}
-
-                \caption{}\label{fig:thickness_step}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_layered.png}
-                \caption{}\label{fig:order_step}
-        \end{subfigure}
-        %MRS: Are (a) and (b) from the nonequilibrium short run?
-        %That's not clear. Not clear it's possible to state that it's
-        %the ``right'' disordered basin if from the end of a short heating run.
-	%BJC: They are from the short run, but as I comment above, I need to 
-	% replace them with the correct figures
-
-	\caption{In all cases, blue lines represent the measured value of
-	the order parameter, black lines are average values calculated from
-	equilibrated Basin B systems at each temperature, green shaded regions
-	represent the standard deviation of each of the black line values, and 
-	red dashed lines show where the temperature is bumped to the next level.
-	(a) At 280K, the system is in a configuration reminiscent of
-	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
-	spacing of Basin A decreases with temperature approaching the value 
-	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
-	temperature but is far from the Basin B value. Longer equilibrations at 
-	each temperature are needed to allow the system to fully expand. 
-        %MRS: might need to explain this ratio better?
-        (e) The ratio 
-	of pore radius to uncertainty for Basin A changes smoothly with temperature,
-	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
-  \end{figure}
-
-  \subsection*{Ionic conductivity calculation}
-
-  %MRS: which model? Be specific as to which of the above structural ensembles was used.
-  The model gives reasonable estimates of ionic conductivity when compared to 
-  experiment.
-  \begin{itemize}
-  	\item Calculated values of ionic conductivity obtained using the Nernst 
-	Einstein relation and Collective Diffusion model are compared in 
-	Table~\ref{table:conductivity}.
-	\item The two methods agree with each other within error, although the 
-	uncertainty obtained using the Collective Diffusion model is much higher.
-	\item Much longer simulations are needed to lower the uncertainty. % TODO: Run Basin B out longer at same conditions as A
-	\item Collective diffusion calculations were generated from 
-	500 ns simulations.
-	\item Our calculated values would benefit from longer simulations. 
-	\item For this reason we will likely only use the Nernst Einstein relation
-	in future calculations of this type. 
-	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
-	\item We hypothesize that conductivity is enhanced in Basin B due to a 
-	higher sodium ion diffusivity.
-	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
-	Sodium ions have less nearby sites to move to in Basin A.
-	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
-	\item In both cases, our calculated values for Basin A are higher than the 
-	experimental values, as expected. 
-	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
-	\item However, the real system, although mostly aligned and straight, has a 
-	distribution of azimuthal angles, meaning that the pores have a degree of 
-	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
-	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
-	fold increase in ionic conductivity. We would expect additional gains in a 
-	perfectly aligned system.
-  \end{itemize}
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
-  \hline
-  Method & Basin A & Basin B \\
-  \midrule
-  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
-  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
-  Experiment & \num{1.33e-5} (0.10) & -- \\
-  \bottomrule
-  \end{tabular}
-  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
-  agree within error. Both methods give calculated values of ionic conductivity which
-  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
-  \end{table}
-
-  %MRS: the next sections maybe should be supporting?
-  %MRS: you say ``the distance decreases by 1 A'' but is that true
-  %over all of the different structures? 
-  %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
-  %MRS: you don't otherwise discuss clearly what effect crosslinking would have. 
-  \subsection*{Implementation of the crosslinking algorithm}
-
-  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
-  Basin A.
-  \begin{itemize}  %BJC: working on the following. The following is what I expect
-  	\item There is an even distribution of crosslinks between same monomer tails, 
-	between monomers in the same pore and between monomers in different pores 
-	including periodic boundaries.
-	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
-	crosslinked
-	\item Major features are still present in the X-ray diffraction
-	\item The ionic conductivity is higher/lower in the crosslinked system
-  \end{itemize}
-  %BJC: THe following figure will be replaced with one representative of the new
-  % data I am  collecting above.
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
-		\caption{}\label{fig:p2p_diagram}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
-		\caption{}\label{fig:no_xlink_p2p}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{xlink_p2p.png}
-		\caption{}\label{fig:xlink_p2p}
-	\end{subfigure}
-	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
-	Each numbered circle represents a pore. Distances are measured along each of the 
-	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
-	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
-	individual pores in the crosslinked system are stable relative to the uncrosslinked
-	system}\label{fig:xlink}
-  \end{figure}
-
-  \section*{Conclusion}
-
-  We have used a detailed molecular model of the Col\textsubscript{h} phase formed by NA-GA3C11
-  in order to study the nanoscopic structure.
-  \begin{itemize}
-  	\item While there have been efforts to model formation of various liquid crystalline 
-	phases with molecular dynamics, to our knowledge there have been no studies which 
-	attempt to examine their structure with the same level of detail presented here.
-	\item We have confirmed that monomers stay partitioned in layers.
-	\item We were able to deduce that layers are composed of 5 monomers.
-	\item We have identified two metastable basins which each consist of a set of 
-	similar monomer configurations characterized by the degree of order in the pore region.
-	\item We verified that the basins are not separate phases.
-	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
-	membrane strucure. 
-	\item Simulated diffration patterns generated from MD trajectories suggest that
-	the offset configuration produces a structure with the closest match to experiment. 
-	\item Even though our model only answers these questions for a system created by 
-	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
-	little extra effort. 
-  \end{itemize}
-
-\clearpage
-\bibliography{llc}
-
 \end{document}

### 2017-09-28 Ben_Manuscripts/Paper1/Outline.tex
updates to BCC topology and BCC initialization procedure

@@
   We will now address the questions raised in the introduction in the order
-  that they were asked.  %BJC: Not a fan of this
+  that they were asked.  %BJC: Not a fan of this transition
 
@@
   its long term stability suggests that it can exist under some conditions.  
-  Basin B is the dominant configuration at higher temperatures.
+  We observed that Basin B is the dominant configuration at higher temperatures.
   \begin{itemize}
@@
 
-  In an attempt to mitigate hysteresis, we performed a slow, stepwise temperature ramp.
-  \begin{itemize}
-        \item Starting from a sandwiched structure equilibrated at 280K, the system
-        temperature was raised to 300K and allowed to equilibrate for 200 ns.
-        \item At the end of 200 ns, the temperature was raised 5K and equilibrated
-        again for 200 ns.
-        \item We continued raising the temperature by 5K and equilibrating for 200 ns
-        until the system was equilibrated for 200 ns at 320K.
-	\item The same process was repeated with a system equilibrated in Basin B and used
-	as a benchmark for comparison. 
+  In an attempt to mitigate hysteresis, we performed slow, stepwise temperature ramps
+  on a parallel displaced and a sandwiched configuration previously equilibrated at 300K.
+  \begin{itemize}
+        \item Every 200 ns, the temperature was raised 5K until we reached 345K
+	\item We performed the same procedure with a system equilibrated in the CP Basin
+	and used it as a benchmark for comparison. 
   \end{itemize}
@@
 
-  Basin A and Basin B are two configurationally metastable basins.
+  The CP and OP basins are two configurationally metastable basins.
   \begin{itemize}
@@
 	existence of two phases (Figure~\ref{fig:phase_transition}).
-	\item Qualitatively, the pore structure of the Basin A system becomes
-        comparable to one characteristic of Basin B as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
-	\item The Basin A system does not converge to the same order parameter
-	values as Basin B, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
+	\item Qualitatively, the pore structure of the OP basin system becomes
+        comparable to one characteristic of the CP basin as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
+	\item The OP basin system does not converge to the same order parameter
+	values as the CP basin, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
 	\item To resolve the quanitative discrepancy, we would need a slower 
@@
 	trajectory, we can conclude that the two basins are not separate phases
-	\item Basin A is the closest match to what is seen experimentally
-	\item Basin B is likely an intermediate between the Col\textsubscript{h} 
+	\item The OP basin is the closest match to what is seen experimentally
+	\item The CP basin is likely an intermediate between the Col\textsubscript{h} 
 	phase and isotropic phase
-	\item Basin B is present in our simulations at lower temperatures 
+	\item The CP basin is present in our simulations at lower temperatures 
         %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
         %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
+	%BJC: Not with what we have because it's in-situ SAXS data which only shows the pore spacing
 	because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
-	stabilize the system into Basin A. 
+	stabilize the system into the OP basin. 
   \end{itemize}
@@
 
-  %MRS: which model? Be specific as to which of the above structural ensembles was used.
+  We use the equilibrated offset system in the OP basin to calculate ionic 
+  conductivity since its structure is the closest match to experiment.
   The model gives reasonable estimates of ionic conductivity when compared to 
@@
 	in future calculations of this type. 
-	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
+  \end{itemize}
+
+  The CP basin has a higher ionic conductivity than the OP basin.
+  \begin{itemize}
 	\item We hypothesize that conductivity is enhanced in Basin B due to a 
@@
   %over all of the different structures?
+  %BJC: limiting the discussion to the OP basin in the offset configuration 
   %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
@@
   We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
-  Basin A.
+  the OP basin.
   \begin{itemize}  %BJC: working on the following. The following is what I expect
@@
 	including periodic boundaries.
+	\item We reach 95 \% conversion of terminal vinyl groups
 	\item The distance between pores shrinks by 1 \angstrom~ after the system is 

### 2017-10-03 Ben_Manuscripts/Paper1/Outline.tex
added forcefield parameters to gaff
Outline updates

@@
 
-  (1) Do monomers partition into and persist as defined monomer layers?
-  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
-  thought to be composed of monomer layers stacked on top of each other. 
-  \begin{itemize}
-  	\item Their existence is supported by experimental evidence of strong 
-	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
-	membrane plane.
-	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
-	leaves no description of what is happening in monomer tail region
-	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
-	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
-  \end{itemize}
-
-  (2) If layers do exist, how many monomers constitute a single layer?
-  There has been no definitive answer to the question in literature.
+%BJC: How question (1) and (2) used to be ordered:
+%
+%  (1) Do monomers partition into and persist as defined monomer layers?
+%  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
+%  thought to be composed of monomer layers stacked on top of each other. 
+%  \begin{itemize}
+%  	\item Their existence is supported by experimental evidence of strong 
+%	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
+%	membrane plane.
+%	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
+%	leaves no description of what is happening in monomer tail region
+%	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
+%	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
+%  \end{itemize}
+%
+%  (2) If layers do exist, how many monomers constitute a single layer?
+%  There has been no definitive answer to the question in literature.
+%  \begin{itemize}
+%    \item A simple molecular simulation study of a similar molecule suggested
+%    that there are 4 monomers in each layer. Their estimation is based on a
+%    simulated system containing only 16 total monomers which likely does not sufficiently
+%    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
+%    \item A separate calculation based on the volume of the liquid crystal monomers proposes
+%    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
+%    \item A molecular model orders of magnitude larger than any other reported atomistic 
+%    liquid crystal membrane simulations has the best chance of directly answering this question.
+%  \end{itemize}
+
+  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
+  into stacked layers which form columnar pores. There has been no definitive
+  answer in literature regarding the number of monomers in each layer. We want to
+  know (1) If layers do exist, how many monomers constitute a single layer?
   \begin{itemize}
@@
     liquid crystal membrane simulations has the best chance of directly answering this question.
+    \item We can directly change the layer composition and note its effect on membrane structure.
+  \end{itemize}
+
+  (2) Does our model support the existence of layers and if so, how well defined
+  are the layers?
+  \begin{itemize}
+       \item Experimentally, their existence is supported by evidence of strong 
+       $\pi$-$\pi$ stacking interactions in the direction perpendicular to the
+       membrane plane.
+       \item $\pi$-$\pi$ stacking will only occur between monomer head groups which
+       leaves no description of what is happening in the monomer tail region
+       \item The tails may entangle isotropically while stacking order is maintained
+       among headgroups. 
+       %\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
+       %with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
   \end{itemize}
@@
     number density.
+    \item To extract the average distance between layers we applied a discrete 
+    fourier transform to the data and extracted the highest intensity frequency 
+    \item We compare the degree of layering between systems based on the 
+    amplitude of the first peak in $g(z)$. We halve the difference between the 
+    maximum of the first peak and the following minimum. We compare the difference
+    to the mean to get a percentage deviation from the average number density.
     \item Our simulations tend to equilibrate to a wider interlayer spacing of
@@
 
-  To answer (1), we verified that the system stays partitioned into layers by
-  plotting the pair correlation function calculated between aromatic rings along
-  the length of the pores (Fig~\ref{fig:zdf}).
+% BJC: How this section (||||) used to be ordered until deciding to put monomers / layer first
+%                        VVVV
+  %To answer (1), we verified that the system stays partitioned into layers by
+  %plotting the pair correlation function calculated between aromatic rings along
+  %the length of the pores (Fig~\ref{fig:zdf}).
   % BJC: add how this calculation is done to methods section (put where I talk about
   % choosing distance between layers
-  \begin{itemize}
-	\item Period of fluctuation (layer spacing)
-        \item Magnitude of fluctuations
-	\item Comment on difference between offset/layered, number of monomers per layer
-  \end{itemize}
+  %\begin{itemize}
+%	\item Period of fluctuation (layer spacing)
+ %       \item Magnitude of fluctuations
+%	\item Comment on difference between offset/layered, number of monomers per layer
+ % \end{itemize}
 
   % BJC: might replace with a figure containing alllllll of the zdf's
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf5layered.png}
-                \caption{}\label{fig:zdf_layered}
-        \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf5offset.png}
-                \caption{}\label{fig:zdf_offset}
-        \end{subfigure}
-        \caption{Pair distribution functions of aromatic carbons for the
-        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
-        parallel displaced configurations. Clear periodic maxima in the 
-        $z$ probability density indicate distinct layers. The magnitude 
-        of the spikes with respect to the average suggest that the 5 
-        monomer per layer, sandwiched configuration possesses a higher 
-        degree of layer partitioning.}\label{fig:zdf}
-  \end{figure}
-
-  To discern the composition of the monomer layers, addressing (2), we ran 
+  %\begin{figure}[!ht]
+%       \centering
+%       \begin{subfigure}{0.45\textwidth}
+%               \centering
+%               \includegraphics[width=\textwidth]{zdf5layered.png}
+%               \caption{}\label{fig:zdf_layered}
+%       \end{subfigure}
+%       \begin{subfigure}{0.45\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf5offset.png}
+%                \caption{}\label{fig:zdf_offset}
+%        \end{subfigure}
+%        \caption{Pair distribution functions of aromatic carbons for the
+%        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
+%        parallel displaced configurations. Clear periodic maxima in the 
+%        $z$ probability density indicate distinct layers. The magnitude 
+%        of the spikes with respect to the average suggest that the 5 
+%        monomer per layer, sandwiched configuration possesses a higher 
+%        degree of layer partitioning.}\label{fig:zdf}
+%  \end{figure}
+
+%  To discern the composition of the monomer layers, addressing (2), we ran 
+%  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
+  %\begin{itemize}
+%  	\item Both the sandwiched and parallel displaced configurations were tested.
+%	\item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
+        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
+	%BJC: Working on getting them all run out to 400 ns
+%	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
+%	\item Systems built with 5 monomers in each layer equilibrate to a pore spacing
+%	that is most consistent with the experimental value of 4.12 nm derived from
+%	SAXS measurements (Figure~\ref{fig:SAXS}).
+%	\item The remainder of this discussion will focus on the analysis of systems
+%	built with 5 monomers per layer. 
+%  \end{itemize}
+
+  To discern the composition of the monomer layers, addressing (1), we ran
   simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
@@
 
+  To answer (2), we verified that the system stays partitioned into layers by
+  plotting the pair correlation function, $g(z)$ calculated between aromatic rings along
+  the length of the pores (Fig~\ref{fig:zdf}).
+  \begin{itemize}
+        \item Sandwiched configuration layers stack 4.29 \angstrom apart while
+        parallel displaced configuration layers stack 4.37 \angstrom apart.
+        The power spectrums used to calculate the reported layer spacing are given in the 
+        Supplemental Information.
+	\item Even though the layer spacing is similar, the sandwiched configuration
+	exhibits more defined layers with its first peak deviating from the mean 
+        number density by 61 \%.
+	\item The parallel displaced configuration deviates from the mean by only 
+	12 \% in comparison.
+  \end{itemize}
+
+  % BJC: might replace with a figure containing alllllll of the zdf's
+  \begin{figure}[!ht]
+        \centering
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf5layered.png}
+                \caption{}\label{fig:zdf_layered}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf5offset.png}
+                \caption{}\label{fig:zdf_offset}
+        \end{subfigure}
+        \caption{Pair distribution functions of aromatic carbons for the
+        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
+        parallel displaced configurations. Clear periodic maxima in the
+        $z$ probability density indicate distinct layers. The magnitude
+        of the spikes with respect to the average suggest that the 5
+        monomer per layer, sandwiched configuration possesses a higher
+        degree of layer partitioning.}\label{fig:zdf}
+  \end{figure}
+
   % BJC: Even though I will shift focus to only 5 monomers per layer, I can put other data
@@
   \midrule
-  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
+  4 & $3.71 \pm 0.04$ & $3.84 \pm 0.02$ \\
   5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
@@
   \end{tabular}
-  \caption{The pore spacing (given in $\nm$) of the model increases as
+  \caption{The pore spacing (given in nm) of the model increases as
   number of monomers in each layer increases. The pore spacing of a system
@@
   per layer in a parallel displaced configuration result in a pore spacing
-  closest to the experimental 4.12 $\nm$~}\label{table:p2p} 
+  closest to the experimental 4.12 nm}
+  \label{table:p2p} 
   \end{table}
@@
   to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
-  with layers stacked 4.0 $\nm$ apart and to our surprise, we observed
+  with layers stacked 4.0 nm apart and to our surprise, we observed
   long-term stability of a qualitatively different configurations suggesting
@@
         \item We will refer to this large set of configurations, with an open pore, as 
-        the OP Basin (open pore) (Figure~\ref{fig:abasin}).
+        the OP Basin (open pore) (Figure~\ref{fig:OPbasin}).
 	\item Simulations of systems built with layers stacked greater than 4 
@@
 	hydrophilic regions.
-	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:bbasin}).
+	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:CPbasin}).
 	\item This LLC membrane may exist in at least two metastable states.
@@
                 \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:abasin}
+                \caption{}\label{fig:OPbasin}
         \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:bbasin}
-        \end{subfigure}
-	\caption{From a qualitative standpoint, Basin A (a) is characterized by a
-	hollow cylindrical pore while pores in Basin B (b) are characterized by a
+                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
+                \caption{}\label{fig:CPbasin}
+        \end{subfigure}
+	\caption{From a qualitative standpoint, the OP Basin (a) is characterized by a
+	hollow cylindrical pore while pores in the CP Basin (b) are characterized by a
 	higher degree of radial disorder}\label{fig:basins}
@@
   experimental structure might be reminiscent of the parallel displaced or sandwiched
-  configurations in the OP or CP basins.
+  configuration in the OP or CP basin.
   %We created systems using three distinct initial configurations and examined
@@
 
-  % Three paragraphs instead here? Talk about disordered, parallel displaced and 
-  % layered separately? Try it. 
-  % Talk about disordered last so it leads in to 
-  % Also maybe don't talk about question 4 until after this
-
+  %BJC: below (commented out) thesis is from when I had the following three paragraphs combined
   %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
@@
 
-  The spots that appear in the simulated XRD pattern of the OP basin
+  R-spots appearing in the simulated XRD pattern of the OP basin
   conformations are a result of the way alkane tails pack together.
@@
   	\item Previously, the spots in the diffraction pattern had been explained 
-	as the product of tilted alkane chains.
+	as the product of tilted alkane chains. % BJC: reference
 	\item We measured the tilt angle of the alkane chains and showed that our 
@@
 	\item By removing atoms from the trajectory and simulating a diffraction 
-	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
+	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails}).
 	\item Since the tails stay nearly flat, we plotted the centroids of the 
@@
 
+  \begin{figure}
+	\centering
+	\begin{subfigure}{0.45\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
+		\caption{}\label{fig:topdown_tails_only}
+	\end{subfigure}
+	\begin{subfigure}{0.45\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{tails_rzplot.png}
+		\caption{}\label{fig:tails_rzplot}
+	\end{subfigure}
+	\caption{(a) All atoms except carbon atoms making up the tails are removed from the 
+	trajectory. (b) The simulated diffraction pattern of the tail-only trajectory still 
+        shows R-spots}\label{fig:tails}
+  \end{figure}
+
   \begin{figure}[ht]
   \centering
-  \begin{subfigure}{0.3\linewidth}
+  	\begin{subfigure}{\linewidth}
+	\centering
+		\begin{subfigure}{0.45\textwidth}
         		\centering
@@
 		\end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
+		\begin{subfigure}{0.45\textwidth}
+		\centering
+	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
+		        \caption{}~\label{fig:layered_tails}
+		\end{subfigure}
+	\end{subfigure}
+	\begin{subfigure}{\linewidth}
+	\centering
+		\begin{subfigure}{0.45\textwidth}
 	        \centering
 		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
-        \caption{}~\label{fig:layered_tails}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{integrated_WAXS_ring.png}
 		        \caption{}~\label{fig:rz_layered}
 		\end{subfigure}
-  \caption{The distribution of angles w.r.t. xy plane between alkane chain tail centroids and nearest
-  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (b) configurations both show
-  distinct peaks at $\pm$ 33 $\degree$. (c) Integrated 2D WAXS data between $q_r$=1 and $q_r$=1.42 shows
-  distinct peaks at with maxima at $\pm$ 37 $\degree$}~\label{fig:tail_packing}
+		\begin{subfigure}{0.45\textwidth}
+        	\centering
+		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
+		        \caption{}~\label{fig:test}
+		\end{subfigure}
+	\end{subfigure}
+  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
+  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
+  same peaks are visible when the 2D simulated diffraction data is radially integrate in the R-alkanes region,
+  (b) and (d) respectively.}~\label{fig:tail_packing}
   \end{figure}
 
-  %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
-  %MRS: we had talked a lot about interconversion (or conversion one way but not other?) but 
-  %MRS: I think things have changed since then? 
+  %BJC: old version of above figure v v v
+  %\begin{figure}[ht]
+  %\centering
+
+  %\begin{subfigure}{0.3\linewidth}
+  %      \centering
+  %      \includegraphics[width=\linewidth]{offset_tail_packing.png}
+  %      \caption{}~\label{fig:offset_tails}
+  %\end{subfigure}
+  %\begin{subfigure}{0.3\linewidth}
+  %      \centering
+  %      \includegraphics[width=\linewidth]{angles_traj_layered.png}
+  %      \caption{}~\label{fig:layered_tails}
+  %\end{subfigure}
+  %\begin{subfigure}{0.3\linewidth}
+  %      \centering
+  %      \includegraphics[width=\linewidth]{integrated_WAXS_ring.png}
+  %      \caption{}~\label{fig:rz_layered}
+  %\end{subfigure}
+  %\caption{The distribution of angles w.r.t. xy plane between alkane chain tail centroids and nearest
+  %neighbor centroids for equilibrated parallel displaced (a) and sandwiched (b) configurations both show
+  %distinct peaks at $\pm$ 33 $\degree$. (c) Integrated 2D WAXS data between $q_r$=1 and $q_r$=1.42 shows
+  %distinct peaks at with maxima at $\pm$ 37 $\degree$}~\label{fig:tail_packing}
+  %\end{figure}
+
   The disordered basin shares little in common with the ordered basin but 
@@
         \item We linearly ramped the temperature of a system in Basin A
-        from 280K to 340K over 100 ns.
+        from 280K to 340K (just below the experimental isotropic transition temperature) over 100 ns.
         \item Visually, there is a distinct change in pore structure from one
-        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
-        Basin B (Figure~\ref{fig:340K_pore}).
+        characteristic of the OP Basin (Figure~\ref{fig:280K_pore}) to one characteristic of
+        the CP Basin (Figure~\ref{fig:340K_pore}).
         \item The slope of all order parameters changes between 315K and 325K
@@
 
-  We can not immediately classify Basin A and Basin B as separate phases.
+  We can not immediately classify the OP Basin and the CP Basin as separate phases.
   \begin{itemize}
@@
                 \centering
-                % these next 2 figures are REALLY big (12-18M). Likely could reduce to near 0.5-1.0 MB without loss of 
-                % necessary resolution.  A few other figures could have resolution reduced.
                 \includegraphics[width=\textwidth]{280K_tramp_close.png}
@@
                 \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
+                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
                 \caption{}\label{fig:340K_pore}
@@
         \caption{(a) The open pore structure exhibited by a structure equilibrated
-        at 280K is characteristic of Basin A. (b) The closed pore structure with
+        at 280K is characteristic of the OP Basin. (b) The closed pore structure with
         a high degree of radial disorder exhibited when the structure in (a) is
-        heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
+        heated to 340K is characteristic of the CP Basin. (c) A plot of distance between pores
         vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
@@
   \begin{itemize}
-        \item There is litle change in disordered phase properties during the 
+        \item There is litle change in CP basin properties during the 
         temperature ramp.
 	\item We observed smooth changes in order parameters as temperature
-        of the Basin A system was increased implying that we cannot claim the
+        of the OP Basin system was increased implying that we cannot claim the
 	existence of two phases (Figure~\ref{fig:phase_transition}).
@@
 	%BJC: Not with what we have because it's in-situ SAXS data which only shows the pore spacing
-	because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
+	than experiment because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
 	stabilize the system into the OP basin. 
@@
                 \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
+                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
                 \caption{}\label{fig:BasinB_340K_pore}
@@
         \end{subfigure}
-        %MRS: Are (a) and (b) from the nonequilibrium short run?
-        %That's not clear. Not clear it's possible to state that it's
-        %the ``right'' disordered basin if from the end of a short heating run.
-	%BJC: They are from the short run, but as I comment above, I need to 
-	% replace them with the correct figures
 
@@
 	each temperature are needed to allow the system to fully expand. 
-        %MRS: might need to explain this ratio better?
-        (e) The ratio 
-	of pore radius to uncertainty for Basin A changes smoothly with temperature,
+        (e) The ratio of pore radius to uncertainty for Basin A changes smoothly with temperature,
 	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}

### 2017-10-09 Ben_Manuscripts/structure_paper/Outline.tex
Rethinking the scope of the paper. Renamed folders to be more descriptive

--- 2017-10-03 Ben_Manuscripts/Paper1/Outline.tex
@@
     \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-    phase. The presence of small amounts of water results in the H\textsubscript{II} 
-    phase.
+    phase. The presence of water results in the H\textsubscript{II} phase.
     \item In both cases, monomers assemble into mesophases made of hexagonally
@@
 %     space} available for membrane design  %BJC: redundant
-    \item Over the past 20 years, HII phase LLC membrane studies have been limited primarily
+    \item Over the past 20 years, H\textsubscript{II} phase LLC membrane studies have been limited primarily
     to Na-GA3C11 with some characterization done after minor structural modifications
@@
     membrane design.
-    \item Molecular dynamics will have the required level of detail
+    \item Molecular dynamics simulations will provide the required level of detail
   \end{itemize}
@@
 	    phase is a simpler starting point, due to the absence of water, and has
-	    equivalent experimental structural data.
+	    more detailed experimental structural data.  % BJC: More detailed because of WAXS. HII doesn't have any (that I know of) WAXS
 	    \item Despite having structural data, there is still information which 
@@
        membrane plane.
-       \item $\pi$-$\pi$ stacking will only occur between monomer head groups which
+       \item $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups which
        leaves no description of what is happening in the monomer tail region
@@
        among headgroups. 
-       %\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
-       %with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
   \end{itemize}
@@
    \begin{itemize}
-      \item A driving force of self assembly in this system is thought to be $\pi$-$\pi$
-      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
+      \item The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly 
+      in this system\cite{gazit_possible_2002} %is thought to be $\pi$-$\pi$ stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
       \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
@@
 
+   (4) Is it necessary to include any water in order to appropriately model the 
+   Col\testsubscript{h} phase?
+   \begin{itemize}
+	\item While the Col\textsubscript{h} phase is described as dry, it is 
+	possible that small amounts of ambient water may be leached into the system.
+	\item The hydrogen bonding network formed by the water may play a role 
+        in structuring the pore.
+	\item We can use simulated X-ray diffraction patterns to see if there is
+        any meaningful structural difference between a dry and "wet" system
+   \end{itemize}
+
 %     \item While we might be able to provide answers to these questions using a 
@@
 
-  (4) Can the system exist in other metastable states or phases that are not
-  accessed during experiments?
-  There remains the possibility that there is more than one metastable state 
-  associated with a given LLC system.
-  \begin{itemize}
-    \item Simulating a membrane atomistically will require many atoms which further
-    limits the timescales acessible with MD
-    \item It is reasonable to expect that we will generate configurations which 
-    are kinetically trapped in a metastable free energy basin
-    \item We must be able to identify which state is produced experimentally and 
-    why others are not.
-  \end{itemize}
-
-  Once we have addressed all of the above questions, we must show that the 
-  developed molecular model is consistent with physical observations so that we
-  can rely on conclusions drawn about structural features characteristic of 
-  the system.
-  \begin{itemize}
-    \item In this study, we build a significantly more realistic atomistic model of LLC membranes 
+%  (4) Can the system exist in other metastable states or phases that are not
+%  accessed during experiments?
+%  There remains the possibility that there is more than one metastable state 
+%  associated with a given LLC system.
+%  \begin{itemize}
+%    \item Simulating a membrane atomistically will require many atoms which further
+%    limits the timescales acessible with MD
+%    \item It is reasonable to expect that we will generate configurations which 
+%    are kinetically trapped in a metastable free energy basin
+%    \item We must be able to identify which state is produced experimentally and 
+%    why others are not.
+%  \end{itemize}
+
+  %Once we have addressed all of the above questions, we must show that the 
+  %developed molecular model is consistent with physical observations so that we
+  %can rely on conclusions drawn about structural features characteristic of 
+  %the system.
+  In this study, we build a significantly more realistic atomistic model of LLC membranes
   than has ever previously been done, and explore what new structural information can be gained
   and what structure hypotheses are supported by this model.
+
+  \begin{itemize}
     \item We validate the model using as much experimental information as possible.
@@
     \item Simulations of greater than 100 ns show no indicators of progress 
-    towards an ordered system.
+    towards an ordered system.  %BJC: include more details in supplment?
     \item To bypass the slow self-assembly process, python scripts are used
@@
 		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
-		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
+		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
   \end{figure}
@@
   in~\cite{feng_scalable_2014}) and small angle X-ray scattering (SAXS) data from~\cite{feng_thin_2016}
-  to inform some of our initial guess choices (Figure~\ref{fig:SWAXS}). We rely primarily
+  to inform our choices of some initial structural parameters (Figure~\ref{fig:SWAXS}). We rely primarily
   on the 2D WAXS data since it encodes all structural details down to the sub-nm scale.
@@
         spacing between packed alkane chains. This reflection will be called R-alkanes.
-        \item Within R-alkanes, are four spots of higher intensity which
+        \item Within R-alkanes, are four spots of higher relative intensity which
         will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
         in their respective quadrants. In many liquid crystal systems this can be
-        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
+        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: References
         \item The first corresponds to the spacing and symmetry of
@@
     apart in the z-direction.
-    \item We extracted the equilibrium distance between layers based on the first
-    peak of a spatial correlation function, $g(z)$, measured along the z-axis (perpendicular to 
-    the membrane plane)
+    \item To quantify the degree of layering in our system, we calculated
+    a spatial correlation function, $g(z)$, measured along the z-axis 
+    (perpendicular to the membrane plane)
     \item To calculate $g(z)$, we binned the z component distances between 
@@
     number density.
-    \item To extract the average distance between layers we applied a discrete 
-    fourier transform to the data and extracted the highest intensity frequency 
     \item We compare the degree of layering between systems based on the
@@
     to the mean to get a percentage deviation from the average number density.
-    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
-    spacings greater than 4 \angstrom~.
+    \item To extract the average distance between layers we applied a discrete 
+    fourier transform to $g(z)$ and extracted the highest intensity frequency 
   \end{itemize}
@@
 
-  We based the pore radii of our initial configuration on past TEM and size exclusion 
-  rejection data
+%  We based the pore radii of our initial configuration on past TEM and size exclusion 
+%  rejection data
   We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
@@
     \item We will not make direct comparisons of pore radius between our model 
-    and experiment to avoid the ambiguity, however, we do define a pore radius based 
+    and experiment to avoid the ambiguity, however, we do define a pore radius  
     for our own purposes.
-    \item To measure the pore radius in our model we calculate the distance between 
-    the center of mass of each aromatic ring and the center of mass of all aromatic rings
-    in their respective pores.
+    %\item To measure the pore radius in our model we calculate the distance between 
+    %the center of mass of each aromatic ring and the center of mass of all aromatic rings
+    %in their respective pores.
   \end{itemize}
@@
     stacking modes will be explored.
-    \item Both have reported stacking distances near 3.7 \angstrom % Reference
+    \item Both have reported stacking distances near the R-$\pi$ value of 3.7 \angstrom % Reference
     \item Headgroups in the sandwiched configuration are stacked directly on top of
@@
 
-  % This can be cut down if C and D prove to be no help. 
-  We tested a number of equilibration schemes of increasing complexity in an effort
-  to match experiment while overcoming kinetic limitations that might trap the system 
-  in a metastable states. All start from an initial configuration generated with 
-  chosen structure variables. 
-  \begin{itemize}
-      \item Equilibration Scheme A:
-      \begin{itemize}
-          \item Steepest descent energy minimization
-          \item Short NPT simulation (~ 5 ns ) with berendsen barostat (tau-p = 1) at 300 K 
-          \item Switch to Parrinello-Rahman (tau-p = 10) and run NPT simulation for 400 - 500 ns
-          %\item Final structure strongly influenced by monomer configuration used to build 
-      \end{itemize}
-      \item Equilibration Scheme B:
+  %We tested a number of equilibration schemes of increasing complexity in an effort
+  %to match experiment while overcoming kinetic limitations that might trap the system 
+  %in a metastable states. All start from an initial configuration generated with 
+  %chosen structure variables.
+  We developed equilibration schemes to create dry and wet configurations. Both schemes 
+  start with an initial configuration generated according to the previous guidelines.
+  \begin{itemize}
+      \item Dry equilibration scheme:
       \begin{itemize}
@@
           \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-          ensemble for 400 - 500 ns in the same way as Scheme A.
-      \end{itemize}
-      \item Equilibration Scheme C:
-      \begin{itemize} 
-          \item A system equilibrated according to scheme B is cut in half so we can access
-          longer simulation timescales
-          \item The system is simulated at 335K, close to its isotropic transition temperature, for 200 ns. % BJC: not entirely sure if it needs to be an already equilibrate structure
-          \item The structure is then linearly cooled back down to 300 K over 500 ns. 
-          \item The system size is doubled back to its original size and equilibrated for 200 ns at 300 K.
-          \item Tried with and without an applied electric field.
-      \end{itemize}
-      \item Equilibration Scheme D:
-      \begin{itemize}
-          \item Even in the near dry Col\textsubscript{h} system, there exists an
-          equilibrium concentration of water.
-          \item The hydrogen bonding network formed by the water may play a role 
-          in structuring the pore.
-          \item We obtained an estimate of equilibrium pore water content by solvating
-          an initial configuration with water baths above and below the membrane. 
-	  \item We ran the solvated system according to Scheme A but for 1000 ns
-          \item Using that number we added water to the pores of an initial 
-	  configuration and equilibrated according to scheme B. 
-      \end{itemize}
-      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1
+          ensemble for at least 400 ns.
+      \end{itemize}
+      \item Wet equilibration scheme: 
+      \begin{itemize}
+	  % BJC: the following three bullet points ended up not being the case since I used significantly less water
+          %\item We obtained an estimate of equilibrium pore water content by solvating
+          %an initial configuration with water baths above and below the membrane. 
+	  %\item We ran the solvated system according to Scheme A but with a 1000 ns equilibration
+          %\item Using that number we added water to the pores of an initial 
+	  %configuration and equilibrated according to scheme B. 
+	  \item In order to create a wet system, we solvated an initial configuration with water using gmx solvate
+          \item All waters placed outside the pore region are removed 
+	  \item Waters inside the pore region are randomly removed until the desired concentration
+	  of water in the pores is reached. 
+	  \item The remainder of the equilibration is the same as the dry system
+      \end{itemize}
+      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1 % BJC: supplemental?
   \end{itemize}
@@
 
-  %\Experimental wide angle X-ray scattering measurements were performed using a 
+  %Experimental wide angle X-ray scattering measurements were performed using a 
   %Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
@@
 
+  % BJC: To be replaced by Joe's description
   Simulated X-ray diffraction patterns were generated based on atomic
@@
   Using an equilibrated structure, a crosslinking procedure was performed
-  in order to better parallel synthetic procedures. 
+  in order to match synthetic procedures. 
   \begin{itemize}
@@
     \item Head-to-tail addition was the only propagation mode considered due to 
-    its dominance the real system.
+    its dominance in the real system.
     \item Direction of attack was not considered because the resultant mixture 
@@
     %MRS: probably. 
-    \item The resulting crosslinked structure has an even distribution of
-    crosslinks between monomer tails of the same monomer, monomers stacked on
-    top of each other and monomers in other pores, including across periodic
-    boundaries.
-    \item The pore spacing shrinks by $\approx$ 1 \angstrom~ and stays 
-    constant under a range of simulation conditions.
+    %\item The resulting crosslinked structure has an even distribution of
+    %crosslinks between monomer tails of the same monomer, monomers stacked on
+    %top of each other and monomers in other pores, including across periodic
+    %boundaries.
+    %\item The pore spacing shrinks by $\approx$ 1 \angstrom~ and stays 
+    %constant under a range of simulation conditions.
   \end{itemize}
@@
         The power spectrums used to calculate the reported layer spacing are given in the 
-        Supplemental Information.
+        Supplemental Information.  %BJC: "Power spectrum" and okay description here?
 	\item Even though the layer spacing is similar, the sandwiched configuration
 	exhibits more defined layers with its first peak deviating from the mean 
-        number density by 61 \%.
+        number density by 61 \%. %BJC: I mention how I do this calculation in the methods. Is it clear that I'm doing that here?
 	\item The parallel displaced configuration deviates from the mean by only 
@@
 
-  % BJC: might replace with a figure containing alllllll of the zdf's
   \begin{figure}[!ht]
@@
 
-  % BJC: Even though I will shift focus to only 5 monomers per layer, I can put other data
+  % BJC: Even though I will shift focus to only 5 monomers per layer, I will put other data
   % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information
@@
 
-  The $z$-direction correlation functions show that layers in our model prefer
-  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
-  with layers stacked 4.0 nm apart and to our surprise, we observed
-  long-term stability of a qualitatively different configurations suggesting
-  that we have found more than one metastable free energy basin.
-  %that the initial distance between layers can influence the approach towards 
-  %equilibrium.
-  \begin{itemize}
-  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
-        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
-	structure.
-        \item We will refer to this large set of configurations, with an open pore, as 
-        the OP Basin (open pore) (Figure~\ref{fig:OPbasin}).
-	\item Simulations of systems built with layers stacked greater than 4 
-	\angstrom~ apart results in a pore structure characterized by high radial 
-	disorder, while still maintaining partitioning between hydrophobic and 
-	hydrophilic regions.
-	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:CPbasin}).
-	\item This LLC membrane may exist in at least two metastable states.
-	\item The distinct difference in pore structure exhibited by each phase will 
-	likely lead to different transport mechanisms.
-	\item Because the pore structure will vary between each Basin, understanding 
-	which phase exists experimentally is necessary in order to ensure we are 
-	studying the system which actually dominates.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:OPbasin}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
-                \caption{}\label{fig:CPbasin}
-        \end{subfigure}
-	\caption{From a qualitative standpoint, the OP Basin (a) is characterized by a
-	hollow cylindrical pore while pores in the CP Basin (b) are characterized by a
-	higher degree of radial disorder}\label{fig:basins}
-  \end{figure}
+%BJC: metastable stuff
+%  The $z$-direction correlation functions show that layers in our model prefer
+%  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
+%  with layers stacked 4.0 nm apart and to our surprise, we observed
+%  long-term stability of a qualitatively different configurations suggesting
+%  that we have found more than one metastable free energy basin.
+%  %that the initial distance between layers can influence the approach towards 
+%  %equilibrium.
+%  \begin{itemize}
+%  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
+%        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
+%	structure.
+%        \item We will refer to this large set of configurations, with an open pore, as 
+%        the OP Basin (open pore) (Figure~\ref{fig:OPbasin}).
+%	\item Simulations of systems built with layers stacked greater than 4 
+%	\angstrom~ apart results in a pore structure characterized by high radial 
+%	disorder, while still maintaining partitioning between hydrophobic and 
+%	hydrophilic regions.
+%	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:CPbasin}).
+%	\item This LLC membrane may exist in at least two metastable states.
+%	\item The distinct difference in pore structure exhibited by each phase will 
+%	likely lead to different transport mechanisms.
+%	\item Because the pore structure will vary between each Basin, understanding 
+%	which phase exists experimentally is necessary in order to ensure we are 
+%	studying the system which actually dominates.
+%  \end{itemize}
+
+%  \begin{figure}[!ht]
+%        \centering
+%        \begin{subfigure}[b]{0.475\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+%                \caption{}\label{fig:OPbasin}
+%        \end{subfigure}
+%        \begin{subfigure}[b]{0.475\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
+%                \caption{}\label{fig:CPbasin}
+%        \end{subfigure}
+%	\caption{From a qualitative standpoint, the OP Basin (a) is characterized by a
+%	hollow cylindrical pore while pores in the CP Basin (b) are characterized by a
+%	higher degree of radial disorder}\label{fig:basins}
+%  \end{figure}
 
@@
 
-  We answer question (3) by simulating X-ray diffraction patterns produced from
-  equilibrated MD trajectories. We leave open the possibility that the 
-  experimental structure might be reminiscent of the parallel displaced or sandwiched
-  configuration in the OP or CP basin.
+% BJC: Re-written without mention of basins in follwoing paragraph
+ % We answer question (3) by simulating X-ray diffraction patterns produced from
+ % equilibrated MD trajectories. We leave open the possibility that the 
+ % experimental structure might be reminiscent of the parallel displaced or sandwiched
+ % configuration in the OP or CP basin.
   %We created systems using three distinct initial configurations and examined
   %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
-  \begin{itemize}
-  	\item OP Basin systems were built in both the parallel displaced and sandwiched 
-	configurations with an intial layer spacing of 3.7 \angstrom~.
-	\item A third system was created by stacking layers in the sandwiched 
-	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
-	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
-	\item The three systems were equilibrated according to our procedure with
-	NPT simulations of greater than 400 ns.
+%  \begin{itemize}
+%  	\item OP Basin systems were built in both the parallel displaced and sandwiched 
+%	configurations with an intial layer spacing of 3.7 \angstrom~.
+%	\item A third system was created by stacking layers in the sandwiched 
+%	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
+%	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
+%	\item The three systems were equilibrated according to our procedure with
+%	NPT simulations of greater than 400 ns.
+%	\item Simulated diffration patterns were generated using portions of the
+%	trajectory after equilibration.  
+%	\item We assume the simulation has equilibrated when the distance between 
+%	pores and the membrane thickness stopped changing.
+%	\item Simulated diffraction patterns for all three structures are shown in 
+%	Figure ~\ref{fig:XRDsim}. 
+%  \end{itemize}
+
+  We answer question (3) by simulating X-ray diffraction patterns produced from
+  equilibrated MD trajectories.
+  %We created systems using three distinct initial configurations and examined
+  %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
+  \begin{itemize}
+	\item We created configurations in both the parallel displaced and sandwiched
+	configurations
+        \item The systems were assembled and equilibrated according to our dry equilibration procedure
         \item Simulated diffration patterns were generated using portions of the
@@
         \item We assume the simulation has equilibrated when the distance between
-	pores and the membrane thickness stopped changing.
-	\item Simulated diffraction patterns for all three structures are shown in 
-	Figure ~\ref{fig:XRDsim}. 
-  \end{itemize}
+        pores and the membrane thickness stopped changing. %BJC: might be better placed in methods
+        \item Simulated diffraction patterns for both structures are shown and 
+	compared to experimenta in Figure ~\ref{fig:XRDsim}.
+  \end{itemize}
+%
 
@@
 
-  Simulated diffraction of the disordered pore structure in the both the sandwiched
-  and parallel displaced configurations does not match the experimental pattern.
-  \begin{itemize}
-        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
-	R-$\pi$ and R-spots are not present. 
-        \item Due to low resolution, making out the individual spots of R-pores is
-        challenging and can be validated with slightly better resolution upon full
-        spherical integration of the 3D structure factor. However, the same
-        information can be extracted by measuring the pore spacing as described earlier.
-        %BJC: ^^^This can be more concise 
-        \item Although the structure's diffraction pattern is very different from
-        experiment, its long-term stability suggests that the structure is realistic.
-	We will explore this further when addressing (4). 
-  \end{itemize}
+%  Simulated diffraction of the disordered pore structure in the both the sandwiched
+%  and parallel displaced configurations does not match the experimental pattern.
+%  \begin{itemize}
+%        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
+%	R-$\pi$ and R-spots are not present. 
+%        \item Due to low resolution, making out the individual spots of R-pores is
+%        challenging and can be validated with slightly better resolution upon full
+%        spherical integration of the 3D structure factor. However, the same
+%        information can be extracted by measuring the pore spacing as described earlier.
+%        %BJC: ^^^This can be more concise 
+%        \item Although the structure's diffraction pattern is very different from
+%        experiment, its long-term stability suggests that the structure is realistic.
+%	We will explore this further when addressing (4). 
+%  \end{itemize}
 
@@
         \item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
-        in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as % update distance if needed
+        in experiment. The rings prefer to stack $\approx 4.2 \angstrom$ apart as % update distance if needed
         opposed to 3.7 \angstrom~.
@@
 
-  R-spots appearing in the simulated XRD pattern of the OP basin
-  conformations are a result of the way alkane tails pack together.
+  R-spots, which appears in both simulated XRD patterns, is a result of the way 
+  alkane tails pack together.
   \begin{itemize}
@@
 	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
-	\item The distribution of these angles is consistent with the location of 
-	the spots (Figure~\ref{fig:tail_packing}).
+	\item We see distinct peaks in the distribution of these angles (Figure~\ref{fig:tail_packing})
+  \end{itemize}
+
+  The peaks in the tail angle distribution are consistent with the location of R-spots.
+  \begin{itemize}
 	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
@@
   \end{figure}
+
+  We answer (4) and further support (3) by preparing parallel displaced and
+  sandwiched configurations according to the wet equilibration procedure.
+  \begin{itemize}
+	\item We do not have an experimental measurement of water in the pores
+	\item We decided the number of waters to put in each pore by estimating
+        the number of hydrogen bonds in which pore entities could participate.
+	\item In solution, each headgroup has a charge of -1
+	\item We estimate there to be about 4 water molecules per layer based 
+	on various packing configurations and geometric constraints
+	\item 4 water molecules per layer translates to about 1.6 wt \%
+  \end{itemize}
 
@@
 
-  The disordered basin shares little in common with the ordered basin but 
-  its long term stability suggests that it can exist under some conditions.  
-  We observed that Basin B is the dominant configuration at higher temperatures.
-  \begin{itemize}
-        \item We linearly ramped the temperature of a system in Basin A
-        from 280K to 340K (just below the experimental isotropic transition temperature) over 100 ns.
-        \item Visually, there is a distinct change in pore structure from one
-        characteristic of the OP Basin (Figure~\ref{fig:280K_pore}) to one characteristic of
-        the CP Basin (Figure~\ref{fig:340K_pore}).
-        \item The slope of all order parameters changes between 315K and 325K
-        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
-        possibility of an abrupt change in system ordering.
-        \item Our 100 ns temperature ramp was likely too fast and caused the system
-        to suffer from hysteresis.
-  \end{itemize}
-
-  We can not immediately classify the OP Basin and the CP Basin as separate phases.
-  \begin{itemize}
-	\item To prove the existence of two phases we need evidence of a
-	a first order phase transition.
-	\item A first order phase transition can be denoted by a discontinuity
-        of some order parameter in response to an external condition such as
-	temperature.
-	\item We chose three easily measurable order parameters: the distance
-	between pores, the membrane thickness and the ratio of pore radius to
-	the uncertainty in pore radius.  % BJC: these may change
-        \item The pore radius is divided by its uncertainty as a way of quantifying
-        the degree to which monomers obstruct the pore region.
-  \end{itemize}
-
-  In an attempt to mitigate hysteresis, we performed slow, stepwise temperature ramps
-  on a parallel displaced and a sandwiched configuration previously equilibrated at 300K.
-  \begin{itemize}
-        \item Every 200 ns, the temperature was raised 5K until we reached 345K
-	\item We performed the same procedure with a system equilibrated in the CP Basin
-	and used it as a benchmark for comparison. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
-                \caption{}\label{fig:340K_pore}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_tramp.png}
-                \caption{}\label{fig:p2p_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_tramp.png}
-
-                \caption{}\label{fig:thickness_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_tramp.png}
-                \caption{}\label{fig:order_tramp}
-        \end{subfigure}
-        \caption{(a) The open pore structure exhibited by a structure equilibrated
-        at 280K is characteristic of the OP Basin. (b) The closed pore structure with
-        a high degree of radial disorder exhibited when the structure in (a) is
-        heated to 340K is characteristic of the CP Basin. (c) A plot of distance between pores
-        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
-        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
-        its uncertainty changes slope near 315K.}\label{fig:tramp}
-  \end{figure}
-
-  The CP and OP basins are two configurationally metastable basins.
-  \begin{itemize}
-        \item There is litle change in CP basin properties during the 
-        temperature ramp.
-	\item We observed smooth changes in order parameters as temperature
-        of the OP Basin system was increased implying that we cannot claim the
-	existence of two phases (Figure~\ref{fig:phase_transition}).
-	\item Qualitatively, the pore structure of the OP basin system becomes
-        comparable to one characteristic of the CP basin as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
-	\item The OP basin system does not converge to the same order parameter
-	values as the CP basin, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
-	\item To resolve the quanitative discrepancy, we would need a slower 
-	temperature ramp
-	\item Since there are no abrupt changes in any order parameter along the 
-	trajectory, we can conclude that the two basins are not separate phases
-	\item The OP basin is the closest match to what is seen experimentally
-	\item The CP basin is likely an intermediate between the Col\textsubscript{h} 
-	phase and isotropic phase
-	\item The CP basin is present in our simulations at lower temperatures 
-        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
-        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
-	%BJC: Not with what we have because it's in-situ SAXS data which only shows the pore spacing
-	than experiment because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
-	stabilize the system into the OP basin. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-	% BJC: I'll get actual pictures of the system here. I'm not sure how 
-	% necessary this figure is though. It could go in the supplemental 
-	% information and I can reference the pictures in the previous figure
-	% since they show basically the same idea : Ordered vs. disordered pore
-	% Alternatively, I could show two diffraction patterns here from the 
-	% beginning and end temperature 
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:BasinA_280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
-                \caption{}\label{fig:BasinB_340K_pore}
-        \end{subfigure}
-	\vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_layered.png}
-                \caption{}\label{fig:p2p_step}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_layered.png}
-
-                \caption{}\label{fig:thickness_step}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_layered.png}
-                \caption{}\label{fig:order_step}
-        \end{subfigure}
-
-	\caption{In all cases, blue lines represent the measured value of
-	the order parameter, black lines are average values calculated from
-	equilibrated Basin B systems at each temperature, green shaded regions
-	represent the standard deviation of each of the black line values, and 
-	red dashed lines show where the temperature is bumped to the next level.
-	(a) At 280K, the system is in a configuration reminiscent of
-	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
-	spacing of Basin A decreases with temperature approaching the value 
-	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
-	temperature but is far from the Basin B value. Longer equilibrations at 
-	each temperature are needed to allow the system to fully expand. 
-        (e) The ratio of pore radius to uncertainty for Basin A changes smoothly with temperature,
-	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
-  \end{figure}
+%BJC: basin stuff that won't be included in this paper
+%  The disordered basin shares little in common with the ordered basin but 
+%  its long term stability suggests that it can exist under some conditions.  
+%  We observed that Basin B is the dominant configuration at higher temperatures.
+%  \begin{itemize}
+%        \item We linearly ramped the temperature of a system in Basin A
+%        from 280K to 340K (just below the experimental isotropic transition temperature) over 100 ns.
+%        \item Visually, there is a distinct change in pore structure from one
+%        characteristic of the OP Basin (Figure~\ref{fig:280K_pore}) to one characteristic of
+%        the CP Basin (Figure~\ref{fig:340K_pore}).
+%        \item The slope of all order parameters changes between 315K and 325K
+%        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
+%        possibility of an abrupt change in system ordering.
+%        \item Our 100 ns temperature ramp was likely too fast and caused the system
+%        to suffer from hysteresis.
+%  \end{itemize}
+
+%  We can not immediately classify the OP Basin and the CP Basin as separate phases.
+%  \begin{itemize}
+%	\item To prove the existence of two phases we need evidence of a
+%	a first order phase transition.
+%	\item A first order phase transition can be denoted by a discontinuity
+%        of some order parameter in response to an external condition such as
+%	temperature.
+%	\item We chose three easily measurable order parameters: the distance
+%	between pores, the membrane thickness and the ratio of pore radius to
+%	the uncertainty in pore radius.  % BJC: these may change
+%        \item The pore radius is divided by its uncertainty as a way of quantifying
+%        the degree to which monomers obstruct the pore region.
+%  \end{itemize}
+
+% In an attempt to mitigate hysteresis, we performed slow, stepwise temperature ramps
+%  on a parallel displaced and a sandwiched configuration previously equilibrated at 300K.
+%  \begin{itemize}
+%        \item Every 200 ns, the temperature was raised 5K until we reached 345K
+%	\item We performed the same procedure with a system equilibrated in the CP Basin
+%	and used it as a benchmark for comparison. 
+%  \end{itemize}
+%
+%  \begin{figure}[!ht]
+%        \centering
+%        \begin{subfigure}[b]{0.475\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+%                \caption{}\label{fig:280K_pore}
+%        \end{subfigure}
+%        \begin{subfigure}[b]{0.475\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
+%                \caption{}\label{fig:340K_pore}
+%        \end{subfigure}
+%        \vskip\baselineskip
+%        \begin{subfigure}[b]{0.325\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{p2p_tramp.png}
+%                \caption{}\label{fig:p2p_tramp}
+%        \end{subfigure}
+%        \begin{subfigure}[b]{0.325\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{thickness_tramp.png}
+%
+%                \caption{}\label{fig:thickness_tramp}
+%        \end{subfigure}
+%        \begin{subfigure}[b]{0.325\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{order_tramp.png}
+%                \caption{}\label{fig:order_tramp}
+%        \end{subfigure}
+%        \caption{(a) The open pore structure exhibited by a structure equilibrated
+%        at 280K is characteristic of the OP Basin. (b) The closed pore structure with
+%        a high degree of radial disorder exhibited when the structure in (a) is
+%        heated to 340K is characteristic of the CP Basin. (c) A plot of distance between pores
+%        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
+%        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
+%        its uncertainty changes slope near 315K.}\label{fig:tramp}
+%  \end{figure}
+
+%  The CP and OP basins are two configurationally metastable basins.
+%  \begin{itemize}
+%        \item There is litle change in CP basin properties during the 
+%        temperature ramp.
+%	\item We observed smooth changes in order parameters as temperature
+%        of the OP Basin system was increased implying that we cannot claim the
+%	existence of two phases (Figure~\ref{fig:phase_transition}).
+%	\item Qualitatively, the pore structure of the OP basin system becomes
+%        comparable to one characteristic of the CP basin as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
+%	\item The OP basin system does not converge to the same order parameter
+%	values as the CP basin, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
+%	\item To resolve the quanitative discrepancy, we would need a slower 
+%	temperature ramp
+%	\item Since there are no abrupt changes in any order parameter along the 
+%	trajectory, we can conclude that the two basins are not separate phases
+%	\item The OP basin is the closest match to what is seen experimentally
+%	\item The CP basin is likely an intermediate between the Col\textsubscript{h} 
+%	phase and isotropic phase
+%	\item The CP basin is present in our simulations at lower temperatures 
+%        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
+%        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
+%	%BJC: Not with what we have because it's in-situ SAXS data which only shows the pore spacing
+%	than experiment because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
+%	stabilize the system into the OP basin. 
+%  \end{itemize} 
+%
+%  \begin{figure}[!ht]
+%        \centering
+%	% BJC: I'll get actual pictures of the system here. I'm not sure how 
+%	% necessary this figure is though. It could go in the supplemental 
+%	% information and I can reference the pictures in the previous figure
+%	% since they show basically the same idea : Ordered vs. disordered pore
+%	% Alternatively, I could show two diffraction patterns here from the 
+%	% beginning and end temperature 
+%        \begin{subfigure}[b]{0.475\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+%                \caption{}\label{fig:BasinA_280K_pore}
+%        \end{subfigure}
+%        \begin{subfigure}[b]{0.475\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
+%                \caption{}\label{fig:BasinB_340K_pore}
+%        \end{subfigure}
+%	\vskip\baselineskip
+%        \begin{subfigure}[b]{0.325\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{p2p_layered.png}
+%                \caption{}\label{fig:p2p_step}
+%        \end{subfigure}
+%        \begin{subfigure}[b]{0.325\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{thickness_layered.png}
+%
+%                \caption{}\label{fig:thickness_step}
+%        \end{subfigure}
+%        \begin{subfigure}[b]{0.325\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{order_layered.png}
+%                \caption{}\label{fig:order_step}
+%        \end{subfigure}
+%
+%	\caption{In all cases, blue lines represent the measured value of
+%	the order parameter, black lines are average values calculated from
+%	equilibrated Basin B systems at each temperature, green shaded regions
+%	represent the standard deviation of each of the black line values, and 
+%	red dashed lines show where the temperature is bumped to the next level.
+%	(a) At 280K, the system is in a configuration reminiscent of
+%	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
+%	spacing of Basin A decreases with temperature approaching the value 
+%	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
+%	temperature but is far from the Basin B value. Longer equilibrations at 
+%	each temperature are needed to allow the system to fully expand. 
+%        (e) The ratio of pore radius to uncertainty for Basin A changes smoothly with temperature,
+%	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
+%  \end{figure}
 

### 2017-10-09 Ben_Manuscripts/structure_paper/figures/xrd.tex
Rethinking the scope of the paper. Renamed folders to be more descriptive

--- 2017-09-28 Ben_Manuscripts/Paper1/Outline.tex
@@
 \usepackage{graphicx}
-\usepackage{wrapfig}
 \usepackage{subcaption}
 \usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
+
 \begin{document}
-  \bibliographystyle{ieeetr}
-  \graphicspath{{./figures/}}
-  \maketitle
-  \section*{Introduction}
-
-  Nanostructured membrane materials have become increasingly popular for 
-  aqueous separations applications such as desalination and biorefinement
-  because they offer the ability to control membrane architecture at the
-  atomic scale allowing the design of solute-specific separation membranes. \cite{humplik_nanostructured_2011}
-  \begin{itemize}
-    \item Most membrane-based aqueous separations of small molecules can 
-    be achieved using reverse osmosis (RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}
-  \end{itemize}
-
-  While RO and NF have seen many advances in the past few decades, they 
-  are far from perfect separation technologies.
-  \begin{itemize}
-    \item \textit{RO membranes}
-    \item Inconsistent performance : Current state-of-the-art RO membranes are unstructured with
-    tortuous and polydisperse diffusion pathways which leads to 
-    inconsistent performance \cite{song_nano_2011}
-    \item High energy requirements : Necessarily high feed pressures 
-    drive up energy requirements which strains developing regions and
-    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
-    \item Separation based on differences in solubility and diffusivity:
-    Moreover, designing RO membranes to achieve targeted separations of 
-    specific solutes is nearly impossible because various solutes dissolve
-    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
-    \item At best, one can exploit these differences to create a functional
-    selective barrier.
-    \item \textit{NF membranes}
-    \item NF was introduced as an intermediate between RO and ultrafiltration,
-    having the ability to separate organic matter and salts on the order of 
-    one nanometer in size.
-    \item Larger and well-defined pores drive down energy requirements while
-    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
-    \item NF is often used as a precursor to reverse osmosis
-    \item Unfortunately, NF membranes, like RO, possess a pore size 
-    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
-  \end{itemize}
-
-  Nanostructured membranes can bypass many of the performance issues which
-  plague traditional NF and RO membranes.
-  \begin{itemize}
-    \item Tune size and functionality of building blocks to control pore
-    size and shape: One can accomplish targeted separations with high 
-    selectivity by tuning shape, size and functionality of the molecular
-    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
-    \item As a result, solute rejecting pores can have their sizes tuned
-    uniformly, resulting in strict size cut-offs.
-    \item Entirely different mechanisms may govern transport in a given
-    nanostructured material which can inspire novel separation techniques.
-  \end{itemize}
-
-  Development of nanostructured materials has been limited by the ability
-  to synthesize and scale various fundamentally sound technologies.
-  \begin{itemize}
-    \item Graphene sheets are atomically thick which results in excellent
-    permeability but defects during manufacturing severely impact 
-    selectivity. \cite{cohen-tanugi_multilayer_2016}
-    \item Molecular dynamics simulations of carbon nanotubes show
-    promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
-    unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
-    \item Zeolites have sub-nm pores with a narrow pore size 
-    distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
-    however, experimental rejection was low and attributed to interstitial
-    defects formed during membrane synthesis \cite{li_desalination_2004}
-    \item There is a need for a scalable nanostructured membrane
-  \end{itemize}
-
-  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
-  aqueous separation applications. 
-  \begin{itemize}
-    \item LLCs share the characteristic ability of nanostructured membrane
-    materials to create highly ordered structures with the added benefits
-    of low cost and synthetic techniques feasible for 
-    large scale production \cite{feng_scalable_2014}
-    \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-    phase. The presence of small amounts of water results in the H\textsubscript{II} 
-    phase.
-    \item In both cases, monomers assemble into mesophases made of hexagonally
-    packed, uniform size, cylinders with hydrophilic groups oriented inward
-    towards the pore center and hydrophobic groups facing outward.
-    \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
-    the monomer named Na-GA3C11 has been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
-    zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
-    \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
-    aligned, resulting in a low flux membrane, slowing research in the field.
-    \item In 2014, Feng et al. showed that the mesophases could be aligned 
-    using a magnetic field with subsequent crosslinking to lock the structure
-    in place \cite{feng_scalable_2014}
-    \item In 2016, Feng et al. showed that the same result could be obtained 
-    using a technique termed soft confinement \cite{feng_thin_2016}.
-    \item Following this breakthrough, research into LLC membranes has been
-    reinvigorated
-  \end{itemize}
-
-  A molecular level understanding of LLC membrane structure, enabled by molecular
-  dynamics simulations, will provide guidelines to reduce the large chemical space
-  available to design monomers for creation of separation-specific membranes.
-  \begin{itemize}
-%     \item LLCs are versatile and controllable with a \textbf{large chemical design
-%     space} available for membrane design  %BJC: redundant
-    \item Over the past 20 years, HII phase LLC membrane studies have been limited primarily
-    to Na-GA3C11 with some characterization done after minor structural modifications
-    \cite{resel_structural_2000}.
-    \item Rejection studies show that this membrane can not perform separations of
-    solutes less than 1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
-    \item  We do not yet understand how to reduce the effective pore size or 
-    how to tune the chemical environment in the nanopores for effective water
-    desalination or small organic molecule separations.
-    \item It will be challenging to efficiently narrow down the large design space in 
-    a laboratory setting without a robust model.
-    \item The only source of predictive modeling has been macroscopic models 
-    which likely do not adequately describe transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
-    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
-    \item Choice of counterion may influence the establishment of a Donnan potential
-    affecting the degree to which the membrane can exclude charged species.
-    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
-    structure which will be crucial to understanding the role of monomer structure in 
-    membrane design.
-    \item Molecular dynamics will have the required level of detail
-  \end{itemize}
-
-  Our approach to constructing a general model will follow the development of a
-  model of a specific LLC membrane with sufficient experimental characterization.
-    \begin{itemize}
-	    \item We have chosen to focus on assemblies formed by Na-GA3C11
-	    \item We have also narrowed our scope to the development of 
-	    a model of the Col\textsubscript{h} phase membrane.
-	    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-	    phase is a simpler starting point, due to the absence of water, and has
-	    equivalent experimental structural data.
-	    \item Despite having structural data, there is still information which 
-	    experiment cannot definitively answer.
-    \end{itemize}
-
-%BJC: the following just seems like filler now that I've reorganized
-%   A clear picture of the nanoscopic LLC membrane structure, gained by building 
-%   a molecular model will provide evidence to answer existing and newly proposed
-%   questions.
-%     \begin{itemize}
-%     \item Despite having structural data, there is still information which 
-%     experiment cannot definitively answer
-%     \end{itemize}
-
-%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
-%BJC: I moved the logic for choice of monomer to system to model to a separate paragraph (above this).
-I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).
-
-%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems.
-That is the main rationale, and it should be made clear fairly early in the introduction.
-Very important to make your story absolutely as clear as possible.
-%BJC: I moved and edited a paragraph that was originally later on to be 2 above this one.
-I think it does a better job addressing points 2 and 3.
-And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)
-
-  Despite having structural data, there is still information which 
-  experiment cannot definitively answer. There are several key 
-  questions that we intend to answer which will be laid out and numbered
-  in subsequent paragraphs.
-
-  (1) Do monomers partition into and persist as defined monomer layers?
-  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
-  thought to be composed of monomer layers stacked on top of each other. 
-  \begin{itemize}
-  	\item Their existence is supported by experimental evidence of strong 
-	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
-	membrane plane.
-	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
-	leaves no description of what is happening in monomer tail region
-	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
-	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
-  \end{itemize}
-
-  (2) If layers do exist, how many monomers constitute a single layer?
-  There has been no definitive answer to the question in literature.
-  \begin{itemize}
-    \item A simple molecular simulation study of a similar molecule suggested
-    that there are 4 monomers in each layer. Their estimation is based on a
-    simulated system containing only 16 total monomers which likely does not sufficiently
-    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
-    \item A separate calculation based on the volume of the liquid crystal monomers proposes
-    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-    \item A molecular model orders of magnitude larger than any other reported atomistic 
-    liquid crystal membrane simulations has the best chance of directly answering this question.
-  \end{itemize}
-
-   (3) How do monomers in each layer position themselves with respect to surrounding 
-   layers?
-%     Even if we knew the number of monomers in each layer, we still would not know how 
-%     monomers in each layer are positioned with respect to other layers. 
-   \begin{itemize}
-      \item A driving force of self assembly in this system is thought to be $\pi$-$\pi$
-      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
-      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
-      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
-      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
-      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
-      attraction which favors the parallel displaced configuration in all cases
-      except where the substitutions are extremely electron withdrawing
-      \cite{waller_hybrid_2006,ringer_effect_2006}.
-      \item We can use simulated X-ray diffration patterns to compare the two 
-      stacking configurations. 
-   \end{itemize}
-
-%     \item While we might be able to provide answers to these questions using a 
-%     molecular model, there remains the possibility that there is more than one 
-%     metastable state associated with a given LLC system.
-
-  (4) Can the system exist in other metastable states or phases that are not
-  accessed during experiments?
-  There remains the possibility that there is more than one metastable state 
-  associated with a given LLC system.
-  \begin{itemize}
-    \item Simulating a membrane atomistically will require many atoms which further
-    limits the timescales acessible with MD
-    \item It is reasonable to expect that we will generate configurations which 
-    are kinetically trapped in a metastable free energy basin
-    \item We must be able to identify which state is produced experimentally and 
-    why others are not.
-  \end{itemize}
-
-  Once we have addressed all of the above questions, we must show that the 
-  developed molecular model is consistent with physical observations so that we
-  can rely on conclusions drawn about structural features characteristic of 
-  the system.
-  \begin{itemize}
-    \item In this study, we build a significantly more realistic atomistic model of LLC membranes 
-    than has ever previously been done, and explore what new structural information can be gained
-    and what structure hypotheses are supported by this model.
-    \item We validate the model using as much experimental information as possible.
-    \item We are most interested in reproducing the conclusions about structure
-    which have been made from X-ray diffraction (XRD) experiments and in matching ionic
-    conductivity measurements~\cite{feng_thin_2016}.
-    \begin{itemize}
-	    \item We have compared simulated X-ray diffraction patterns to experiment in 
-	    order to match major features present in the 2D patterns.
-	    \item We calculated ionic conductivity using two agreeing methods.
-	    \item We examined the the influence of crosslinking on membrane structure.
-    \end{itemize}
-    \item The structure-building approach and analysis used in this paper can be readily extended
-    to the H\textsubscript{II} phase and other similar LC systems.
-  \end{itemize}
-
-  \section*{Methods}
-
-  Liquid crystal monomers were parameterized using the Generalized AMBER Forcefield
-  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
-  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
-  assigned using tools from Openeye Scientific Software. All molecular dynamics 
-  simulations were run using the latest version of Gromacs 2016. 
-  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-
-  An ensemble of characteristic, low-energy vacuum monomer configurations
-  were constructed by applying a simulated annealing process to a
-  parameterized monomer.
-  \begin{itemize}
-    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
-    \item A low energy configuration was randomly pulled from the trajectory
-    and charges were reassigned using the am1bccsym method of molcharge
-    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
-    \item Using the new charges, the monomer system was annealed again and monomer
-    configurations were pulled from the trajectory to be used for full
-    system construction (Figure~\ref{fig:python}a).
-  \end{itemize}
-
-  The timescale for self assembly of monomers into the hexagonal phase is
-  unknown and likely outside of a reasonable length for an atomistic
-  simulation, calling for a more efficient way to build the system. 
-  \begin{itemize}
-    \item Previous work has shown a coarse grain model self assemble into
-    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
-    \item We attempted atomistic self-assembly by packing monomers into a box 
-    using Packmol \cite{martinez_packmol:_2009}.
-    \item Simulations of greater than 100 ns show no indicators of progress 
-    towards an ordered system.
-    \item To bypass the slow self-assembly process, python scripts are used
-    to assemble monomers into a structure close to one of a number of 
-    hypothesized equilibrium configurations (Figure~\ref{fig:python}).
-   \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
-	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
-		configuration. (b) Monomers are rotated and assembled into layers with 
-		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
-		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
-  \end{figure}
-
-  A typical simulation volume contains four pores in a monoclinic unit cell,
-  the smallest unit cell that maintains hexagonal symmetry when extended 
-  periodically.
-  \begin{itemize}
-    \item Each pore is made of twenty stacked monomer layers with periodic 
-    continuity in the z direction, avoiding any edge effects and creating an 
-    infinite length pore ideal for studying transport.
-    \item A small number of layers is preferred in order to reduce computational
-    cost and to allow us to look at longer timescales.
-    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
-    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
-    This point will be explained in more detail later.
-    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
-    %BJC: so refer to supporting info here?
-Then put plots of diffraction data with different sized system there.
-I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense.
-And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
-    \item We chose initial guesses for the remaining structural parameters based on
-    experimental data and treated them as variables during model development.
-  \end{itemize}
-
-  We used experimental wide angle X-ray scattering (WAXS) data (produced as described 
-  in~\cite{feng_scalable_2014}) and small angle X-ray scattering (SAXS) data from~\cite{feng_thin_2016}
-  to inform some of our initial guess choices (Figure~\ref{fig:SWAXS}). We rely primarily
-  on the 2D WAXS data since it encodes all structural details down to the sub-nm scale.
-  \begin{itemize}
-        \item There are five major features of interest present in the 2D experimental
-        pattern shown in Figure~\ref{fig:WAXS}.
-        \item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
-        corresponding to a real spacing of 3.7 \angstrom~. The reflection is
-        attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-        perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
-        reflection will be referred to as R-$\pi$.
-        \item A weak intensity line is located at exactly half the $q_z$ value of
-        R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a
-        real space periodic spacing of 7.4 \angstrom~. This reflection has been
-        interpreted  as 2\textsubscript{1} helical ordering of aromatic rings
-        along the z axis meaning if the positions of the aromatic rings can
-        be traced by a helix, then for each turn in the helix, there should be
-        two aromatic rings. For this reason it will be referred to as R-helix.
-        \item A third major reflection is marked by a low intensity ring located
-        at r = 1.4 \angstrom$^-1$. The real space separation
-        corresponds to 4.5 \angstrom~ which is characteristic of the average
-        spacing between packed alkane chains. This reflection will be called R-alkanes.
-        \item Within R-alkanes, are four spots of higher intensity which
-        will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
-        in their respective quadrants. In many liquid crystal systems this can be
-        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
-        \item The first corresponds to the spacing and symmetry of
-        the d\textsubscript{100} plane which can be related to the distance between
-        pores. The feature, which will be called R-pores, is characterized by dots
-        along $q_z$ = 0. The spacing between dots is indicative of the hexagonal
-        symmetry of the packed pores. The same information at higher resolution is obtained using a SAXS
-        setup. By radially integrating the 2D data one gets a 1D curve which is 
-        shown in Figure~\ref{fig:SAXS}.  % BJC: I also have 2D SAXS data
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[t]{0.43\linewidth}
-                \centering
-        %       \vspace{12mm}
-                \includegraphics[width=\linewidth]{SAXS.png}
-                \caption{}\label{fig:SAXS}
-        \end{subfigure}
-        \begin{subfigure}[t]{0.47\linewidth}
-                \centering
-                \raisebox{.2\textwidth}{%
-                \includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-                }
-                \caption{}\label{fig:WAXS}
-        \end{subfigure}
-        \caption{(a) 2D wide angle X-ray scattering gives details about repeating
-        features less than 1 nanometer apart. (b) 1D small angle X-ray scattering
-        indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
-  \end{figure}
-
-%  We chose an initial layer spacing based on experimental 2D WAXS data.
-%  \begin{itemize}  
-%    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
-%    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
-%    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
-%    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-%    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
-%    spacings greater than 4 \angstrom~.
-%  \end{itemize}
-
-  We chose the initial layer spacing based on R-$\pi$.
-  \begin{itemize}  
-    \item Each monomer was rotated so the plane of the aromatic head groups would
-    be parallel to the xy plane.
-    \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
-    apart in the z-direction.
-    \item We extracted the equilibrium distance between layers based on the first
-    peak of a spatial correlation function, $g(z)$, measured along the z-axis (perpendicular to 
-    the membrane plane)
-    \item To calculate $g(z)$, we binned the z component distances between 
-    the center of mass of each benzene ring and all others of the same pore 
-    over 50 ns of equilibrated trajectory and then normalized by the average
-    number density.
-    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
-    spacings greater than 4 \angstrom~.
-  \end{itemize}
-
-  We placed pores at a chosen initial spacing based on R-pores, then allowed
-  the system to settle into its preferred spacing. 
-  \begin{itemize}
-    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
-    %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
-    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
-    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
-    resulting from a tightly packed initial configuration.
-    \item To calculate the equilibrated pore spacing, we measured the distance between pore
-    centers.
-    \item Pore centers were located by averaging the coordinates of sodium ions in their 
-    respective pores.
-    \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
-    %BJC: Do bootstrapping details go in supplemental?
-    	% Supplemental vvvv
-	\begin{itemize}
-    	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
-    	sampling from the original trajectory
-    	\item Each pore spacing has its own trajectory with its own average value
-    	\item The average value of each pore spacing is averaged to get the overall
-    	average pore spacing. 
-    	\item The standard deviation of average values is reported as the uncertainty in pore spacing
-    	% BJC: The following will go in supplemental
-        \item We are interested in 5 pore-to-pore distances which should all be equal in 
-        a perfect hexagonal array. Only 4 are independent  
-        % Supplemental ^^^^
-	\end{itemize}
-  \end{itemize}
-
-  %MRS: pore radius is a different category isn't it? Is this an input piece of data?
-  % should be put in a different category.
-  %BJC: Well I still have to initially place the monomers some distance away from the pore
-  % centers. That distance is informed by the experimental evidence.
-
-  We based the pore radii of our initial configuration on past TEM and size exclusion 
-  rejection data
-  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
-  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
-  of pore radius in the initial configuration.
-  \begin{itemize}
-    \item Experimental evidence suggests uniform pores with radii of 0.6 nm 
-    \item Comparing a geometric measurement of pore size derived from an atomistic model,
-    to a less precise, experimentally derived pore size estimate, will give ambiguous results.
-    \item What is meant by pore radius will not be clear until we establish a clear picture
-    of the nanoscopic pore environment.
-    \item When constructing pores, we chose the carboxylate carbon from the monomer
-    head group as a reference atom, and placed it a distance r from the pore center,
-    where r is the pore radius. (See Supplemental Information) %BJC: figure making that clear
-    \item We will not make direct comparisons of pore radius between our model 
-    and experiment to avoid the ambiguity, however, we do define a pore radius based 
-    for our own purposes.
-    \item To measure the pore radius in our model we calculate the distance between 
-    the center of mass of each aromatic ring and the center of mass of all aromatic rings
-    in their respective pores.
-  \end{itemize}
-
-  The relative interlayer orientation was chosen based on clues from 
-  diffraction data as well as the various known stacking modes of benzene 
-  and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
-  ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
-  \begin{itemize}
-    \item The T-shaped configuration was ruled out based on the inconsistency of
-    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
-    \item The system's preference towards the sandwiched vs. parallel displaced 
-    stacking modes will be explored.
-    \item Both have reported stacking distances near 3.7 \angstrom % Reference
-    \item Headgroups in the sandwiched configuration are stacked directly on top of
-    each other while stacked headgroups in the parallel displaced configuration are offset 
-    by $180/nmon$ degrees where $nmon$ equals the number of monomers per layer.
-    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
-    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
-    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.
-This is what we fix, this is what we leave as a variable.
-The analysis probably belongs later.
-    %BJC: Yeah, I will leave the rest for discussion
-%     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
-%     suggests entropic differences based on the way the tails are able to pack.
-%     \item In the sandwiched configuration, all tails start out directly on top
-%     of each other which may prevent closely stacked benzene rings.
-%     \item In the offset configuration, the tails are placed in between each other 
-%     which may allow layers to come together in a compact way.
-%     \item This difference may explain, in part, which stacking mode is more favorable.
-  \end{itemize}
-
-  % This can be cut down if C and D prove to be no help. 
-  We tested a number of equilibration schemes of increasing complexity in an effort
-  to match experiment while overcoming kinetic limitations that might trap the system 
-  in a metastable states. All start from an initial configuration generated with 
-  chosen structure variables. 
-  \begin{itemize}
-      \item Equilibration Scheme A:
-      \begin{itemize}
-          \item Steepest descent energy minimization
-          \item Short NPT simulation (~ 5 ns ) with berendsen barostat (tau-p = 1) at 300 K 
-          \item Switch to Parrinello-Rahman (tau-p = 10) and run NPT simulation for 400 - 500 ns
-          %\item Final structure strongly influenced by monomer configuration used to build 
-      \end{itemize}
-      \item Equilibration Scheme B:
-      \begin{itemize}
-          \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-          configurations while allowing monomer tails to settle.
-          \item Doing so also mitigates system dependence on initial monomer configuration.
-          \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
-          \item Every 50 ps, we reduce the force constants by the square root of its
-          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
-          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
-          slowly released until there is no more restraining potential.
-          \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-          ensemble for 400 - 500 ns in the same way as Scheme A.
-      \end{itemize}
-      \item Equilibration Scheme C:
-      \begin{itemize} 
-          \item A system equilibrated according to scheme B is cut in half so we can access
-          longer simulation timescales
-          \item The system is simulated at 335K, close to its isotropic transition temperature, for 200 ns. % BJC: not entirely sure if it needs to be an already equilibrate structure
-          \item The structure is then linearly cooled back down to 300 K over 500 ns. 
-          \item The system size is doubled back to its original size and equilibrated for 200 ns at 300 K.
-          \item Tried with and without an applied electric field.
-      \end{itemize}
-      \item Equilibration Scheme D:
-      \begin{itemize}
-          \item Even in the near dry Col\textsubscript{h} system, there exists an
-          equilibrium concentration of water.
-          \item The hydrogen bonding network formed by the water may play a role 
-          in structuring the pore.
-          \item We obtained an estimate of equilibrium pore water content by solvating
-          an initial configuration with water baths above and below the membrane. 
-	  \item We ran the solvated system according to Scheme A but for 1000 ns
-          \item Using that number we added water to the pores of an initial 
-	  configuration and equilibrated according to scheme B. 
-      \end{itemize}
-      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1
-  \end{itemize}
-
-%  An equilibration scheme with position restraints placed on aromatic rings
-  %MRS: 
-  %prevents 
-%  during early equilibration steps is required to prevent high energy repulsions .
-  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
-  %BJC: 'high energy repulsions' ?
-%  \begin{itemize}
-%    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-%    configurations while allowing monomer tails to settle.
-%    \item Doing so also mitigates system dependence on initial monomer configuration.
-%    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
-%    \item Every 50 ps, we reduce the force constants by the square root of its 
-%    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
-%    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
-%    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
-%    restraining potential.  
-%    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-%    ensemble for 400 - 500 ns.
-   %BJC: I will reference an equilibration script that can be released with the supplemental info
-   %MRS: we should release as many scripts as is feasible, can be in a github repository.
-   %BJC: Okay, once we submit, I will need to spend some time cleaning the scripts
-   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
-   %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
-%  \end{itemize}
-
-  %BJC: the following paragraph will be replaced with something that Joe writes
-  %MRS: sounds good.
-
-  % BJC: The following methodology is taken from the 2014 Feng et al. paper where
-  % WAXS is reported. The data we are using comes from the 2016 paper which 
-  % I assume used the same set up but I will need to verify this with Xunda
-  % before this gets sent out. The SAXS is the same as shown in the 2016 paper
-  % however I will likely reproduce it with matplotlib
-
-  %\Experimental wide angle X-ray scattering measurements were performed using a 
-  %Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
-  %($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
-  %calibrations of the resultant 2-D WAXS patterns were done by using a 
-  %silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
-  %patterns were integrated into 1-D plots of scattering intensity (I) versus
-  %q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
-  %2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.
-
-  Simulated X-ray diffraction patterns were generated based on atomic
-  coordinates for a direct experimental comparison.
-  \begin{itemize}
-    \item All atomic coordinates were simulated as gaussian spheres of electron
-    density corresponding to each atom's atomic number.
-    \item A three dimensional fourier transform (FT) of the array of electron 
-    density results in a three dimensional structure factor which represents
-    the unit cell in reciprocal space.
-   % \item We perform an angular average of the structure factor about the 
-    z axis to generate a 2D cross section close to what one would see 
-    experimentally.
-    \item We matched experimental 2D WAXS patterns by iterative improvement
-    of our choice of initial structure and equilibration procedure.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{}\label{fig:sandwiched}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{PD.png}
-		\caption{}\label{fig:pd}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{}\label{fig:tshaped}
-	\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwichedlayers.png}
-		\caption{}\label{fig:sandwichedlayers}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{offsetlayers.png}
-		\caption{}\label{fig:offsetlayers}
-	\end{subfigure}
-	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
-	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
-	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
-	configuration }\label{fig:stacking}
-  \end{figure}
-
-  We calculated ionic conductivity using two different methods for robustness.
-  \begin{itemize}
-    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
-    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
-    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
-    \item Sodium ion diffusion coefficients were found by calculating the slope
-    of the linear region of the mean square displacement curve as indicated by
-    the einstein relation \cite{einstein_investigations_1956}.]
-    %MRS: state how you decided which was the linear region.
-    %BJC: nothing fancy other than looking at the msd plot and determining where to
-    % start fitting. I suppose I could minimize R^2 but that seems like overkill
-    \item We looked at the MSD plot to determine where to begin and end a linear fit
-    \item Ion concentration was measured with respect to the entire unit cell. 
-    \item The second method, termed the 'Collective Diffusion' model, measures 
-    the movement of the collective variable, Q, which is defined as the amount
-    of charge transfer through the system and can be thought to represent
-    the center of charge of the system.
-    \item The conductance, $\gamma$ of the system can be calculated as:
-    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
-    achieved by multiplying by channel length and dividing by the membrane
-    cross sectional area.
-    \item $D_Q$ is the diffusion coefficient of the collective variable Q. It can
-    be calculated using the einstein relation.
-    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
-  \end{itemize}
-
-  Using an equilibrated structure, a crosslinking procedure was performed
-  in order to better parallel synthetic procedures. 
-  \begin{itemize}
-    \item The purpose of crosslinking is to maintain macroscopic alignment of 
-    the crystalline domains, ensuring aligned, hexagonally packed pores.
-    \item For that reason, we are not concerned with replicating the kinetics 
-    of the reaction, but instead emphasize the consistency of the final structure
-    with experimental structural data.
-    \item The algorithm was developed based on the known reaction mechanism.
-    \item Crosslinking of this system is a free radical polymerization (FRP)
-    taking place between terminal vinyl groups present on each of the three
-    monomer tails.
-    \item FRPs require an initiator which bonds to the system, meaning new atoms
-    were introduced into the system.
-    \item For simplicity, the initiator was simulated as hydrogen and made present 
-    in the simulation by including them in all possible bonding positions as dummy atoms.
-    \item The crosslinking procedure is carried out iteratively.
-    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
-    \item The topology is updated with new bonds and dummy hydrogen atoms are 
-    changed to appropriate hydrogen types. 
-    \item Head-to-tail addition was the only propagation mode considered due to 
-    its dominance the real system.
-    \item Direction of attack was not considered because the resultant mixture 
-    is racemic.
-    %BJC: The following items belongs in results/discussion
-    %MRS: probably. 
-    \item The resulting crosslinked structure has an even distribution of
-    crosslinks between monomer tails of the same monomer, monomers stacked on
-    top of each other and monomers in other pores, including across periodic
-    boundaries.
-    \item The pore spacing shrinks by $\approx$ 1 \angstrom~ and stays 
-    constant under a range of simulation conditions.
-  \end{itemize}
-
-  \section*{Results and Discussion}
-
-  \subsection*{Determination of Nanoscopic Structural Details}
-
-  %In order to construct an initial configuration which gives reliable 
-  %trends, we need to understand the composition of layers, how far apart
-  %to stack the layers, and how to orient them with respect to each other.
-  %\begin{itemize
-  %	\item To verify our choices for each parameter, we compare our calculations
-  %	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
-  %	scattering (WAXS), and ionic conductivity measurements.
-  %\end{itemize}
-
-  We will now address the questions raised in the introduction in the order
-  that they were asked.  %BJC: Not a fan of this transition
-
-  To answer (1), we verified that the system stays partitioned into layers by
-  plotting the pair correlation function calculated between aromatic rings along
-  the length of the pores (Fig~\ref{fig:zdf}).
-  % BJC: add how this calculation is done to methods section (put where I talk about
-  % choosing distance between layers
-  \begin{itemize}
-	\item Period of fluctuation (layer spacing)
-        \item Magnitude of fluctuations
-	\item Comment on difference between offset/layered, number of monomers per layer
-  \end{itemize}
-
-  % BJC: might replace with a figure containing alllllll of the zdf's
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf5layered.png}
-                \caption{}\label{fig:zdf_layered}
-        \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf5offset.png}
-                \caption{}\label{fig:zdf_offset}
-        \end{subfigure}
-        \caption{Pair distribution functions of aromatic carbons for the
-        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
-        parallel displaced configurations. Clear periodic maxima in the 
-        $z$ probability density indicate distinct layers. The magnitude 
-        of the spikes with respect to the average suggest that the 5 
-        monomer per layer, sandwiched configuration possesses a higher 
-        degree of layer partitioning.}\label{fig:zdf}
-  \end{figure}
-
-  To discern the composition of the monomer layers, addressing (2), we ran 
-  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
-  \begin{itemize}
-  	\item Both the sandwiched and parallel displaced configurations were tested.
-	\item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
-        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
-	%BJC: Working on getting them all run out to 400 ns
-	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
-	\item Systems built with 5 monomers in each layer equilibrate to a pore spacing
-	that is most consistent with the experimental value of 4.12 nm derived from
-	SAXS measurements (Figure~\ref{fig:SAXS}).
-	\item The remainder of this discussion will focus on the analysis of systems
-	built with 5 monomers per layer. 
-  \end{itemize}
-
-  % BJC: Even though I will shift focus to only 5 monomers per layer, I can put other data
-  % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  		   & \multicolumn{2}{c}{Starting Configuration} \\
-  \hline
-  Monomers per layer & Sandwiched & Parallel Displaced \\
-  \midrule
-  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
-  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
-  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
-  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
-  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
-  \bottomrule
-  \end{tabular}
-  \caption{The pore spacing (given in $\nm$) of the model increases as
-  number of monomers in each layer increases. The pore spacing of a system
-  starting in the sandwiched configuration is systematically lower than 
-  that started in an offset configuration. Systems built with 5 monomers
-  per layer in a parallel displaced configuration result in a pore spacing
-  closest to the experimental 4.12 $\nm$~}\label{table:p2p} 
-  \end{table}
-
-%  To answer question (3) we require high resolution experimental evidence which we 
-%  can match to our simulations. Experimental WAXS measurements encode all structural
-%  details and we would like to match them as well as possible. 
-%  %MRS: also encodes the pore spacing
-%  %BJC: got rid of 'remaining' in 'remaining structural details'
-%  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
-%  \begin{itemize}
-%  	\item There are five major features present in the 2D experimental 
-%	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
-%	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
-%	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
-%	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-%	perpendicular to the membrane plane, or z-axis. For simplicity, this 
-%	reflection will be referred to as R-$\pi$.
-%       %MRS: why R in R-pi? for reflection?
-%	%BJC: yes, R = reflection
-%	\item A weak intensity line is located at exactly half the $q_z$ value of
-%	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
-%	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
-%	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
-%	along the z axis meaning if the positions of the aromatic rings can
-%	be traced by a helix, then for each turn in the helix, there should be
-%	two aromatic rings. For this reason it will be referred to as R-helix.
-%	\item A third major reflection is marked by a low intensity ring located
-%	at r = 1.4 \angstrom$^-1$. The real space separation 
-%	corresponds to 4.5 \angstrom~ which is characteristic of the average 
-%	spacing between packed alkane chains. This reflection will be called R-alkanes.
-%	\item Within R-alkanes, are four spots of higher intensity which 
-%	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
-%	in their respective quadrants. In many liquid crystal systems this can be
-%	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
-%	\item The final major reflections correspond to the spacing and symmetry of 
-%	the d\textsubscript{100} plane which can be related to the distance between
-%	pores. The feature, which will be called R-pores, is characterized by dots 
-%	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
-%	symmetry of the packed pores. It is easiest to interpret the data by 
-%	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
-%  \end{itemize}
-
-%  \begin{figure}[!ht]
-%	\centering
-%	\begin{subfigure}[t]{0.47\linewidth}
-%		\centering
-%		\raisebox{.2\textwidth}{%
-%		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-%		}
-%		\caption{}\label{fig:WAXS}
-%	\end{subfigure}
-%	\begin{subfigure}[t]{0.43\linewidth}
-%		\centering
-	%	\vspace{12mm}
-%		\includegraphics[width=\linewidth]{SAXS.png}
-%		\caption{}\label{fig:SAXS}
-%	\end{subfigure}
-%	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
-%	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
-%	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
-        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
-	%BJC: 1D is from a Yale paper. I'm going to remake the figure from the raw data but will reference that
-	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
-%  \end{figure}
-
-  The $z$-direction correlation functions show that layers in our model prefer
-  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
-  with layers stacked 4.0 $\nm$ apart and to our surprise, we observed
-  long-term stability of a qualitatively different configurations suggesting
-  that we have found more than one metastable free energy basin.
-  %that the initial distance between layers can influence the approach towards 
-  %equilibrium.
-  \begin{itemize}
-  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
-        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
-	structure.
-        \item We will refer to this large set of configurations, with an open pore, as 
-        the OP Basin (open pore) (Figure~\ref{fig:abasin}).
-	\item Simulations of systems built with layers stacked greater than 4 
-	\angstrom~ apart results in a pore structure characterized by high radial 
-	disorder, while still maintaining partitioning between hydrophobic and 
-	hydrophilic regions.
-	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:bbasin}).
-	\item This LLC membrane may exist in at least two metastable states.
-	\item The distinct difference in pore structure exhibited by each phase will 
-	likely lead to different transport mechanisms.
-	\item Because the pore structure will vary between each Basin, understanding 
-	which phase exists experimentally is necessary in order to ensure we are 
-	studying the system which actually dominates.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:abasin}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:bbasin}
-        \end{subfigure}
-	\caption{From a qualitative standpoint, Basin A (a) is characterized by a
-	hollow cylindrical pore while pores in Basin B (b) are characterized by a
-	higher degree of radial disorder}\label{fig:basins}
-  \end{figure}
-
-  % BJC: This paragraph needs to change since, upon inspection, it appears that the 
-  % offset configuration is correct. So it needs to shine a more positive light on offset
-  % BJC: I think it can be deleted
-  %We varied the initial relative interlayer orientation between sandwiched and 
-  %parallel-displaced based on our knowledge of the stability of the two
-  %pi-stacking modes.
-  %\begin{itemize}
-  %	\item We generated simulated X-ray diffraction patterns using simulation 
-  %      trajectories from the highly restrained initial configurations created during 
-  %	equilibration
-  %	\item The simulated patterns establish a difference between the two stacking 
-  %	modes (Figure~\ref{fig:XRDrestrained}).
-  %	\item In each pattern, R-alkanes is present at a distance of $\approx
-  %	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
-  %	\item R-$\pi$ is also present in each pattern, although it appears to 
-  %	intersect R-alkanes because the spacing between aromatic rings is 
-  %	similar to the alkane chain packing.
-  %     %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
-  %	%BJC: okay added some more specific language
-  %	\item The difference in aromatic ring spacing between experiment and
-  %	simulation is likely a result of the inability of GAFF to properly handle
-  %	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
-  %	\item The sandwiched configuration shows R-spots in the expected location.
-  %	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
-  %	\item The parallel displaced configuration contains two lines of high 
-  %	intensity with maximum intensity occurring where they intersect the alkane
-  %	chain region due to constructive interference between the two features.
-  %	\item The lines are located where one would expect to see R-helix and, 
-  %	perhaps coincidentally, the intersection with R-alkanes occurs where one 
-  %	would expect to see R-spots.
-	%BJC: might save the following sentence for equilibrium trajectories
-  %	\item As the simulation is progressed, the full line begins to fade 
-  %	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
-  %	where R-helix exists.
-  %\end{itemize}
-
-  %\begin{figure}[!ht]
-  %	\centering
-  %	\begin{subfigure}{0.475\textwidth}
-  %		\hspace{-1.2cm}
-  %		\centering
-  %		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
-  %		\caption{}\label{fig:rzplayeredrestrained}
-  %	\end{subfigure}
-  %	\begin{subfigure}{0.475\textwidth}
-  %		\hspace{-1.2cm}
-  %		\centering
-  %		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
-  %		\caption{}\label{fig:rzoffsetrestrained}
-  %	\end{subfigure}
-  %	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
-  %	with restraints placed on aromatic carbons shows all major features
-  %	present in experimental WAXS. Near solid lines at constant z are a result of 
-  %	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
-  %	restrained parallel displaced configuration may also contain all
-  %	major experimental WAXS features. One can argue that R-spots is not present
-  %	but it is difficult to distinguish because of its intersection with the solid
-  %	R-helix line. 
-        %MRS: Longer simulations are necessary to determine which structure
-	% is the best match to experiment
-        %MRS: we probably want to avoid saying this (above) if we can.
-%}\label{fig:XRDrestrained}
-%  \end{figure}
-
-  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.
-Something to think about.
-  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
-  %MRS: make sure the figures are comparable.
-Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
-
-  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  %patterns produced from equilibrated MD trajectories shows the most consistency
-  %with the offset configuration in the OP basin.
-
-  We answer question (3) by simulating X-ray diffraction patterns produced from
-  equilibrated MD trajectories. We leave open the possibility that the 
-  experimental structure might be reminiscent of the parallel displaced or sandwiched
-  configurations in the OP or CP basins.
-  %We created systems using three distinct initial configurations and examined
-  %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
-  \begin{itemize}
-  	\item OP Basin systems were built in both the parallel displaced and sandwiched 
-	configurations with an intial layer spacing of 3.7 \angstrom~.
-	\item A third system was created by stacking layers in the sandwiched 
-	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
-	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
-	\item The three systems were equilibrated according to our procedure with
-	NPT simulations of greater than 400 ns.
-	\item Simulated diffration patterns were generated using portions of the
-	trajectory after equilibration.  
-	\item We assume the simulation has equilibrated when the distance between 
-	pores and the membrane thickness stopped changing.
-	\item Simulated diffraction patterns for all three structures are shown in 
-	Figure ~\ref{fig:XRDsim}. 
-  \end{itemize}
-
-  % Three paragraphs instead here? Talk about disordered, parallel displaced and 
-  % layered separately? Try it. 
-  % Talk about disordered last so it leads in to 
-  % Also maybe don't talk about question 4 until after this
-
-  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  %patterns shows the most consistency with the offset configuration in the OP basin.
-
-  Simulated diffraction of the disordered pore structure in the both the sandwiched
-  and parallel displaced configurations does not match the experimental pattern.
-  \begin{itemize}
-        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
-	R-$\pi$ and R-spots are not present. 
-        \item Due to low resolution, making out the individual spots of R-pores is
-        challenging and can be validated with slightly better resolution upon full
-        spherical integration of the 3D structure factor. However, the same
-        information can be extracted by measuring the pore spacing as described earlier.
-        %BJC: ^^^This can be more concise 
-        \item Although the structure's diffraction pattern is very different from
-        experiment, its long-term stability suggests that the structure is realistic.
-	We will explore this further when addressing (4). 
-  \end{itemize}
-
-  Simulated XRD of the sandwiched configuration contains all experimental features
-  except for R-helix.
-  \begin{itemize}
-        \item R-alkanes and R-pores appear in the expected locations.
-        \item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
-        in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as % update distance if needed
-        opposed to 3.7 \angstrom~.
-        \item Most notably, R-spots appears in the expected location, which suggests 
-        that there is something intrinsic to closer packing that gives rise 
-        to such features. 
-  \end{itemize}
-
-  The parallel displaced configuration results in a simulated XRD pattern with 
-  the closest match to experiment. 
-  \begin{itemize}
-	\item It produces the only pattern that exhibits all major reflections
-	\item R-alkanes, R-pores and R-$\pi$ appear as they do in the sandwiched configuration. 
-	\item R-spots appears, however with a lower intensity relative to R-alkanes
-        when compared to the sandwiched configuration.
-        \item R-helix appears apparently due to the parallel displaced aromatic rings
-        %BJC: Maybe a figure to explain why this happens
-  \end{itemize}
-
-% BJC: Replacement figure below this one
-%  \begin{figure}[!ht]
-%	\centering
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
-%		\caption{}\label{fig:sandwich_rzplot}
-%	\end{subfigure}
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{offset_rzplot.png}
-%		\caption{}\label{fig:offsetrzplot}
-%	\end{subfigure}
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{disorder_rzplot.png}
-%		\caption{}\label{fig:disorder_rzplot.png}
-%	\end{subfigure}
-%	\caption{(a) All major features except R-helix are present in
-%	XRD patterns resulting from an equilibrated sandwiched configuration 
-%	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
-%	(b) All major features execpt R-spots are present in XRD patterns 
-%	resulting from an equilibrated parallel displaced configuration in Basin A.
-%	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
-%	are the only major features present in XRD patterns resulting from an 
-%	equilibrated disordered phase}\label{fig:XRDsim}
- % \end{figure}
 
 \begin{figure}[ht]
+
 \begin{subfigure}{.83\linewidth}
@@
 		\centering
-                \includegraphics[width=\linewidth, trim={2.5cm 0 4cm 2cm}, clip]{WAXS_raw.png}%
+		\includegraphics[width=\linewidth, trim={2.5cm 0 4cm 1.25cm}, clip]{WAXS_raw.png}%
 		\caption{}~\label{fig:raw_waxs}	
@@
 
-  The spots that appear in the simulated XRD pattern of the OP basin
-  conformations are a result of the way alkane tails pack together.
-  \begin{itemize}
-  	\item Previously, the spots in the diffraction pattern had been explained 
-	as the product of tilted alkane chains.
-	\item We measured the tilt angle of the alkane chains and showed that our 
-	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
-	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
-	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
-        that the spots arise as a consequence of the tails. 
-	\item By removing atoms from the trajectory and simulating a diffraction 
-	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
-	\item Since the tails stay nearly flat, we plotted the centroids of the 
-	tails and measured the angle between each centroid and its nearest neighbors
-	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
-	\item The distribution of these angles is consistent with the location of 
-	the spots (Figure~\ref{fig:tail_packing}).
-	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
-	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
-	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
-	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
-        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
-        is a reconcilable difference with our simulated results.  
-  \end{itemize}
-
-  \begin{figure}[ht]
-  \centering
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{offset_tail_packing.png}
-        \caption{}~\label{fig:offset_tails}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{angles_traj_layered.png}
-        \caption{}~\label{fig:layered_tails}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{integrated_WAXS_ring.png}
-        \caption{}~\label{fig:rz_layered}
-  \end{subfigure}
-  \caption{The distribution of angles w.r.t. xy plane between alkane chain tail centroids and nearest
-  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (b) configurations both show
-  distinct peaks at $\pm$ 33 $\degree$. (c) Integrated 2D WAXS data between $q_r$=1 and $q_r$=1.42 shows
-  distinct peaks at with maxima at $\pm$ 37 $\degree$}~\label{fig:tail_packing}
-  \end{figure}
-
-  %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
-  %MRS: we had talked a lot about interconversion (or conversion one way but not other?) but 
-  %MRS: I think things have changed since then? 
-  The disordered basin shares little in common with the ordered basin but 
-  its long term stability suggests that it can exist under some conditions.  
-  We observed that Basin B is the dominant configuration at higher temperatures.
-  \begin{itemize}
-        \item We linearly ramped the temperature of a system in Basin A
-        from 280K to 340K over 100 ns.
-        \item Visually, there is a distinct change in pore structure from one
-        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
-        Basin B (Figure~\ref{fig:340K_pore}).
-        \item The slope of all order parameters changes between 315K and 325K
-        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
-        possibility of an abrupt change in system ordering.
-        \item Our 100 ns temperature ramp was likely too fast and caused the system
-        to suffer from hysteresis.
-  \end{itemize}
-
-  We can not immediately classify Basin A and Basin B as separate phases.
-  \begin{itemize}
-	\item To prove the existence of two phases we need evidence of a
-	a first order phase transition.
-	\item A first order phase transition can be denoted by a discontinuity
-        of some order parameter in response to an external condition such as
-	temperature.
-	\item We chose three easily measurable order parameters: the distance
-	between pores, the membrane thickness and the ratio of pore radius to
-	the uncertainty in pore radius.  % BJC: these may change
-        \item The pore radius is divided by its uncertainty as a way of quantifying
-        the degree to which monomers obstruct the pore region.
-  \end{itemize}
-
-  In an attempt to mitigate hysteresis, we performed slow, stepwise temperature ramps
-  on a parallel displaced and a sandwiched configuration previously equilibrated at 300K.
-  \begin{itemize}
-        \item Every 200 ns, the temperature was raised 5K until we reached 345K
-	\item We performed the same procedure with a system equilibrated in the CP Basin
-	and used it as a benchmark for comparison. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                % these next 2 figures are REALLY big (12-18M). Likely could reduce to near 0.5-1.0 MB without loss of 
-                % necessary resolution.  A few other figures could have resolution reduced.
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:340K_pore}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_tramp.png}
-                \caption{}\label{fig:p2p_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_tramp.png}
-
-                \caption{}\label{fig:thickness_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_tramp.png}
-                \caption{}\label{fig:order_tramp}
-        \end{subfigure}
-        \caption{(a) The open pore structure exhibited by a structure equilibrated
-        at 280K is characteristic of Basin A. (b) The closed pore structure with
-        a high degree of radial disorder exhibited when the structure in (a) is
-        heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
-        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
-        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
-        its uncertainty changes slope near 315K.}\label{fig:tramp}
-  \end{figure}
-
-  The CP and OP basins are two configurationally metastable basins.
-  \begin{itemize}
-        \item There is litle change in disordered phase properties during the 
-        temperature ramp.
-	\item We observed smooth changes in order parameters as temperature
-        of the Basin A system was increased implying that we cannot claim the
-	existence of two phases (Figure~\ref{fig:phase_transition}).
-	\item Qualitatively, the pore structure of the OP basin system becomes
-        comparable to one characteristic of the CP basin as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
-	\item The OP basin system does not converge to the same order parameter
-	values as the CP basin, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
-	\item To resolve the quanitative discrepancy, we would need a slower 
-	temperature ramp
-	\item Since there are no abrupt changes in any order parameter along the 
-	trajectory, we can conclude that the two basins are not separate phases
-	\item The OP basin is the closest match to what is seen experimentally
-	\item The CP basin is likely an intermediate between the Col\textsubscript{h} 
-	phase and isotropic phase
-	\item The CP basin is present in our simulations at lower temperatures 
-        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
-        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
-	%BJC: Not with what we have because it's in-situ SAXS data which only shows the pore spacing
-	because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
-	stabilize the system into the OP basin. 
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-	% BJC: I'll get actual pictures of the system here. I'm not sure how 
-	% necessary this figure is though. It could go in the supplemental 
-	% information and I can reference the pictures in the previous figure
-	% since they show basically the same idea : Ordered vs. disordered pore
-	% Alternatively, I could show two diffraction patterns here from the 
-	% beginning and end temperature 
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:BasinA_280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:BasinB_340K_pore}
-        \end{subfigure}
-	\vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_layered.png}
-                \caption{}\label{fig:p2p_step}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_layered.png}
-
-                \caption{}\label{fig:thickness_step}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_layered.png}
-                \caption{}\label{fig:order_step}
-        \end{subfigure}
-        %MRS: Are (a) and (b) from the nonequilibrium short run?
-        %That's not clear. Not clear it's possible to state that it's
-        %the ``right'' disordered basin if from the end of a short heating run.
-	%BJC: They are from the short run, but as I comment above, I need to 
-	% replace them with the correct figures
-
-	\caption{In all cases, blue lines represent the measured value of
-	the order parameter, black lines are average values calculated from
-	equilibrated Basin B systems at each temperature, green shaded regions
-	represent the standard deviation of each of the black line values, and 
-	red dashed lines show where the temperature is bumped to the next level.
-	(a) At 280K, the system is in a configuration reminiscent of
-	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
-	spacing of Basin A decreases with temperature approaching the value 
-	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
-	temperature but is far from the Basin B value. Longer equilibrations at 
-	each temperature are needed to allow the system to fully expand. 
-        %MRS: might need to explain this ratio better?
-        (e) The ratio 
-	of pore radius to uncertainty for Basin A changes smoothly with temperature,
-	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
-  \end{figure}
-
-  \subsection*{Ionic conductivity calculation}
-
-  We use the equilibrated offset system in the OP basin to calculate ionic 
-  conductivity since its structure is the closest match to experiment.
-  The model gives reasonable estimates of ionic conductivity when compared to 
-  experiment.
-  \begin{itemize}
-  	\item Calculated values of ionic conductivity obtained using the Nernst 
-	Einstein relation and Collective Diffusion model are compared in 
-	Table~\ref{table:conductivity}.
-	\item The two methods agree with each other within error, although the 
-	uncertainty obtained using the Collective Diffusion model is much higher.
-	\item Much longer simulations are needed to lower the uncertainty. % TODO: Run Basin B out longer at same conditions as A
-	\item Collective diffusion calculations were generated from 
-	500 ns simulations.
-	\item Our calculated values would benefit from longer simulations. 
-	\item For this reason we will likely only use the Nernst Einstein relation
-	in future calculations of this type. 
-  \end{itemize}
-
-  The CP basin has a higher ionic conductivity than the OP basin.
-  \begin{itemize}
-	\item We hypothesize that conductivity is enhanced in Basin B due to a 
-	higher sodium ion diffusivity.
-	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
-	Sodium ions have less nearby sites to move to in Basin A.
-	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
-	\item In both cases, our calculated values for Basin A are higher than the 
-	experimental values, as expected. 
-	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
-	\item However, the real system, although mostly aligned and straight, has a 
-	distribution of azimuthal angles, meaning that the pores have a degree of 
-	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
-	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
-	fold increase in ionic conductivity. We would expect additional gains in a 
-	perfectly aligned system.
-  \end{itemize}
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
-  \hline
-  Method & Basin A & Basin B \\
-  \midrule
-  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
-  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
-  Experiment & \num{1.33e-5} (0.10) & -- \\
-  \bottomrule
-  \end{tabular}
-  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
-  agree within error. Both methods give calculated values of ionic conductivity which
-  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
-  \end{table}
-
-  %MRS: the next sections maybe should be supporting?
-  %MRS: you say ``the distance decreases by 1 A'' but is that true
-  %over all of the different structures?
-  %BJC: limiting the discussion to the OP basin in the offset configuration 
-  %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
-  %MRS: you don't otherwise discuss clearly what effect crosslinking would have. 
-  \subsection*{Implementation of the crosslinking algorithm}
-
-  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
-  the OP basin.
-  \begin{itemize}  %BJC: working on the following. The following is what I expect
-  	\item There is an even distribution of crosslinks between same monomer tails, 
-	between monomers in the same pore and between monomers in different pores 
-	including periodic boundaries.
-	\item We reach 95 \% conversion of terminal vinyl groups
-	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
-	crosslinked
-	\item Major features are still present in the X-ray diffraction
-	\item The ionic conductivity is higher/lower in the crosslinked system
-  \end{itemize}
-  %BJC: THe following figure will be replaced with one representative of the new
-  % data I am  collecting above.
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
-		\caption{}\label{fig:p2p_diagram}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
-		\caption{}\label{fig:no_xlink_p2p}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{xlink_p2p.png}
-		\caption{}\label{fig:xlink_p2p}
-	\end{subfigure}
-	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
-	Each numbered circle represents a pore. Distances are measured along each of the 
-	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
-	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
-	individual pores in the crosslinked system are stable relative to the uncrosslinked
-	system}\label{fig:xlink}
-  \end{figure}
-
-  \section*{Conclusion}
-
-  We have used a detailed molecular model of the Col\textsubscript{h} phase formed by NA-GA3C11
-  in order to study the nanoscopic structure.
-  \begin{itemize}
-  	\item While there have been efforts to model formation of various liquid crystalline 
-	phases with molecular dynamics, to our knowledge there have been no studies which 
-	attempt to examine their structure with the same level of detail presented here.
-	\item We have confirmed that monomers stay partitioned in layers.
-	\item We were able to deduce that layers are composed of 5 monomers.
-	\item We have identified two metastable basins which each consist of a set of 
-	similar monomer configurations characterized by the degree of order in the pore region.
-	\item We verified that the basins are not separate phases.
-	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
-	membrane strucure. 
-	\item Simulated diffration patterns generated from MD trajectories suggest that
-	the offset configuration produces a structure with the closest match to experiment. 
-	\item Even though our model only answers these questions for a system created by 
-	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
-	little extra effort. 
-  \end{itemize}
-
-\clearpage
-\bibliography{llc}
-
 \end{document}

### 2017-10-09 Ben_Manuscripts/structure_paper/results.tex
Rethinking the scope of the paper. Renamed folders to be more descriptive

--- 2017-08-07 Ben_Manuscripts/Paper1/results.tex
@@
 scattering (WAXS) experiments, layers are stacked 3.7 \angstrom apart.
-A characteristic of equilibrated systems simulated in this way, is a
+A characteristic of equilibrated systems set up in this way, is a
 defined, cylindrical and open pore structure. Benzene rings arrange in
-a helical conformation after equilbration. The membrane is about 8 nm
-thick. We will refer to this system as Phase A. (Fig ~\ref{fig:phaseA})
-Simulations of systems built with layers stacked > 4 \angstrom apart
-results in a pore structure characterized by high radial disorder,
-while maintaining partitioning between hydrophobic and hydrophilic
-regions. This will be called phase B (Fig~\ref{fig:phaseB})
+a helical conformation after equilbration. We will refer to this system
+as Basin A (Fig ~\ref{fig:phaseA}). Simulations of systems built with
+layers stacked > 4 \angstrom apart results in a pore structure 
+characterized by high radial disorder, while maintaining partitioning 
+between hydrophobic and hydrophilic regions. This will be called Basin
+B (Fig~\ref{fig:phaseB}).
 % The arrangement of sodium ions (which are closely bound to carbonyl
@@
 to appropriately study the system.
-%Like phase A, phase B can form at 280K. 
-%The phase is also present when phase A is heated close to its isotropic transition point
-%There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
+% Like Basin A, Basin B can form at 280K. 
+% The phase is also present when phase A is heated close to its isotropic transition point
+% There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
 
@@
 For simplicity, this reflection will be referred to as R-pi. A weak intensity
-line is located at exactly half the qz value of R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
-real space periodic spacing of 7.4 \angstroms. This reflection has been 
-attributed to 2\textsubscript{1} helical ordering of aromatic rings along the
-z axis and will therefore be referred to as R-helix. If positions of the 
-aromatic rings can be traced by a helix, then for each turn in the helix, 
-there should be two aromatic rings. A third major reflection is marked by 
-a low intensity ring located at r = 1.4 \angstrom \textsuperscript{-1}. The
-real space separation corresponds to 4.5 \angstroms which is characteristic
-of the average spacing between packed alkane chains. This reflection will be
-called R-alkanes. Within R-alkanes, are four spots of higher intensity which 
-will be called R-spots. All are located \approx 40 degrees from the qz axis
+line is located at exactly half the qz value of R-pi (qz = 0.85 \angstrom 
+\textsuperscript{-1}), corresponding to a real space periodic spacing of 
+7.4 \angstroms. This reflection has been attributed to 2\textsubscript{1}
+helical ordering of aromatic rings along the z axis and will therefore be
+referred to as R-helix. If positions of the aromatic rings can be traced
+by a helix, then for each turn in the helix, there should be two aromatic 
+rings. A third major reflection is marked by a low intensity ring located
+at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
+corresponds to 4.5 \angstroms which is characteristic of the average spacing
+between packed alkane chains. This reflection will be called R-alkanes. 
+Within R-alkanes, are four spots of higher intensity which will be called
+R-spots. All are located \approx 40 degrees from the qz axis
 in their respective quadrants. In many liquid crystal systems this can be
-attributed to the tilt angle of the alkane chains with respect to the xy axis. 
+attributed to the tilt angle of the alkane chains with respect to the xy plane. 
 The final major reflections correspond to the spacing and symmetry of the d100 
@@
         \begin{itemize}
-                \item Phase A
+                \item Basin A
                 \begin{itemize}

### 2017-10-09 Ben_Manuscripts/structure_paper/supplemental.tex
Rethinking the scope of the paper. Renamed folders to be more descriptive

--- 2017-08-18 Ben_Manuscripts/Masters_Bypass/results.tex
@@
-\section*{Results and Discussion}
-\subsection*{Determination of system structural details}
-In order to construct an initial configuration which gives reliable 
-trends, we need to understand the composition of layers, how far apart
-to stack the layers, and how to orient them with respect to each other.
-To verify our choices for each parameter, we compare our calculations
-to experimental small angle X-ray scattering (SAXS), wide angle X-ray
-scattering (WAXS), and ionic conductivity measurements.
+\documentclass{article}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+\usepackage{subcaption}
+\usepackage[margin=1in]{geometry}
+\usepackage{amsmath} % or simply amstext
+\usepackage{siunitx}
+\usepackage{booktabs}
+\usepackage[export]{adjustbox}
+\newcommand{\angstrom}{\textup{\AA}}
+\usepackage{cleveref}
+\usepackage{booktabs}
+\usepackage{gensymb}
+\usepackage{float}
 
-To discern the composition of the monomer layers, we ran simulations of 
-systems created with 4 - 8 monomers per layer. Both the sandwiched and 
-parallel displaced configurations were tested. All systems remained
-stable for at least 50 ns. Pore spacings were calculated by measuring
-the distance between the pore centers. Pore centers were located by
-averaging the coordinates of sodium ions in their respective pores. 
-Statistics were generated using the bootstrapping technique. Table
-~\ref{table:p2p} shows the pore spacing for all systems tested.
-Systems built with 5 monomers in each layer equilibrate to a pore
-spacing that is most consistent with the experimental value of 4.12 nm
-derived from SAXS measurements (Figure~\ref{fig:SAXS}). The remainder of
-this discussion will focus on the analysis of systems built with 5 
-monomers per layer. Pair correlation functions calculated between 
-aromatic rings along the length of the pores indicate that systems
-prefer to stay partitioned into layers (Fig~\ref{fig:zdf}).
+\title{Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
+\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}
 
-\begin{table}[H]
-\centering
-\begin{tabular}{ccc}
-\toprule
-                   & \multicolumn{2}{c}{Starting Configuration} \\
-\hline
-Monomers per layer & Sandwiched & Parallel Displaced \\
-\midrule
-4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
-5 & $3.99 \pm 0.04$ & $4.16 \pm 0.04$ \\
-6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
-7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
-8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
-\bottomrule
-\end{tabular}
-\caption{The pore spacing of the model increases as number of monomers
-in each layer increases. The pore spacing of a system starting in the 
-sandwiched configuration is systematically lower than that started in an 
-offset configuration. Systems built with 5 monomers per layer in a parallel
-displaced configuration results in a pore spacing closest to experimental
-data}\label{table:p2p} 
-\end{table}
+\begin{document}
 
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5layered.png}
-		\caption{}\label{fig:zdf_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{zdf5offset.png}
-		\caption{}\label{fig:zdf_offset}
-	\end{subfigure}
-	\caption{Pair distribution functions of aromatic carbons for the
-	(a) 5 monomer per layer, sanwiched and (b) 5 monomer per layer, 
-	parallel displaced configurations. Spikes in the distribution mark
-	distinct layers. The magnitude of the spikes with respect to the 
-	average suggest that the 5 monomer per layer, sandwiched configuration
-	possesses the highest degree of layer partitioning.}\label{fig:zdf}
-\end{figure}
-
-Experimental WAXS measurements encode all structural details. 
-There are five major features present in the 2D experimental pattern which
-our model intends to reproduce (Figure~\ref{fig:WAXS}). The first is located
-at qz = 1.7 \angstrom \textsuperscript{-1}, corresponding to a real spacing 
-of 3.7 \angstrom. The reflection is attributed to pi-pi stacking
-between aromatic rings in the direction perpendicular to the membrane plane, or z-axis. 
-For simplicity, this reflection will be referred to as R-pi. A weak intensity
-line is located at exactly half the qz value of R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
-real space periodic spacing of 7.4 \angstrom. This reflection has been 
-interpreted  as 2\textsubscript{1} helical ordering of aromatic rings along the
-z axis and will therefore be referred to as R-helix. If positions of the 
-aromatic rings can be traced by a helix, then for each turn in the helix, 
-there should be two aromatic rings. A third major reflection is marked by 
-a low intensity ring located at r = 1.4 \angstrom \textsuperscript{-1}. The
-real space separation corresponds to 4.5 \angstrom which is characteristic
-of the average spacing between packed alkane chains. This reflection will be
-called R-alkanes. Within R-alkanes, are four spots of higher intensity which 
-will be called R-spots. All are located $\approx 40$ degrees from the qz axis
-in their respective quadrants. In many liquid crystal systems this can be
-explained by the tilt angle of the alkane chains with respect to the xy plane. 
-The final major reflections correspond to the spacing and symmetry of the d\textsubscript{100} 
-plane which can be related to the distance between pores. The feature, which 
-will be called R-pores, is characterized by dots along qz = 0. The spacing
-between dots is indicative of the hexagonal symmetry of the packed pores. It
-is easiest to interpret the data by radially integrating the 2D data to get 
-a 1D curve which is shown in Figure~\ref{fig:SAXS}.
-
-\begin{figure}
-	\centering
-	\begin{subfigure}[t]{0.47\linewidth}
-		\centering
-		\raisebox{.2\textwidth}{%
-		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-		}
-		\caption{}\label{fig:WAXS}
-	\end{subfigure}
-	\begin{subfigure}[t]{0.43\linewidth}
-		\centering
-	%	\vspace{12mm}
-		\includegraphics[width=\linewidth]{SAXS.png}
-		\caption{}\label{fig:SAXS}
-	\end{subfigure}
-	\caption{(a) 2D wide angle X-ray scattering gives details about repeating features less than 1 nanometer apart.
-(b) 1D small angle X-ray scattering indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
-\end{figure}
-
-The initial distance between layers can influence the approach towards
-equilibrium. Equilibrated systems built according to the 3.7 \angstrom 
-spacing indicated by R-pi are characterized by a defined, cylindrical and
-open pore structure. Aromatic rings are arranged in a helical conformation.
-We will refer to this system as Basin A (Figure~\ref{fig:280K_pore}). Simulations
-of systems built with layers stacked greater than 4 \angstrom apart results in a pore
-structure characterized by high radial disorder, while still maintaining 
-partitioning between hydrophobic and hydrophilic regions. This will be 
-called Basin B (Figure~\ref{fig:340K_pore}). It is apparent that this LLC membrane
-may exist in at least two metastable states. The distinct difference in 
-pore structure exhibited by each phase will likely lead to different transport
-mechanisms. Understanding which phase exists experimentally is necessary in 
-order to appropriately study the system.
-% BJC: include more examples of the difference between the two basins
-% The arrangement of sodium ions (which are closely bound to carbonyl
-% head groups) can be well-approximated by a gaussian distribution 
-% Like phase A, phase B can form at 280K. 
-% The phase is also present when phase A is heated close to its isotropic transition point
-% There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
-
-Basin A and Basin B are two configurationally metastable basins. 
-We hesitate to classify the basins as separate phases. We hypothesize
-that Basin B is present at higher temperatures. This is evidenced by
-a simulation of a system in Basin A whose temperature was linearly
-ramped from 280K to 340K over 100 ns. Visually, there is a distinct
-change in pore structure from one characteristic of Basin A 
-(Figure~\ref{fig:280K_pore}) to one characteristic of Basin B 
-(Figure~\ref{fig:340K_pore}). To quantify our observation, we chose 
-three easily measurable order parameters: the distance between pores,
-the membrane the thickness and the ratio of pore radius to the uncertainty
-in pore radius. The distance between pores was measured as described 
-previously. The membrane thickness was measured using the length of the
-z box vector. The pore radius was measured by calculating the distance
-between the center of mass of each aromatic ring and the center of mass
-of all aromatic rings in their respective pores. The pore radius is divided by
-its uncertainty in order to understand the degree to which monomers 
-obstruct the pore region. Referring back to our temperature ramped system,
-the slope of all order parameters change around 315K - 325K 
-(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
-possibility of an abrupt change in system ordering. To prove that the 
-basins are in fact two different phases, we must observe evidence of a
-first order phase transition, which would be marked by a discontinuity
-in an order parameter as a function of temperature. Our 100 ns temperature
-ramp may have been too fast causing the system to suffer from hysteresis. To mitigate
-hysteresis, we performed a slow, stepwise temperature ramp. Starting from
-structures equilibrated at 280K, the system temperature was raised to 
-300K and allowed to equilibrate for 200 ns. At the end of 200 ns, the
-temperature was raised 5K and equilibrated again for 200 ns. We repeated
-this process until the system was equilibrated for 200 ns at 320K. In all
-cases, we observed smooth changes in order parameters as temperature was
-increased implying that we can not yet claim the existence of two phases (Figure~\ref{fig:phase_transition}).
-The same process will continue to be repeated up to 340K in the near future
-since we have not surpassed the temperatures where we observe abrupt slope 
-changes in pore spacing and membrane thickness (\Cref{fig:p2p_tramp,fig:thickness_tramp}).
-
-\begin{figure}
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:280K_pore}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close.png}
-                \caption{}\label{fig:340K_pore}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{p2p_tramp.png}
-                \caption{}\label{fig:p2p_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{thickness_tramp.png}
-
-                \caption{}\label{fig:thickness_tramp}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.325\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{order_tramp.png}
-                \caption{}\label{fig:order_tramp}
-        \end{subfigure}
-        \caption{(a) The open pore structure exhibited by a structure equilibrated
-	at 280K is characteristic of Basin A. (b) The closed pore structure with 
-	a high degree of radial disorder exhibited when the structure in (a) is 
-	heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
-	vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs. 
-	temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
-	its uncertainty changes slope near 315K.}\label{fig:tramp}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_layered.png}
-		\caption{}\label{fig:p2p_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{thickness_layered.png}
-		\caption{}\label{fig:thickness_layered}
-	\end{subfigure}
-	\begin{subfigure}{0.325\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{order_layered.png}
-		\caption{}\label{fig:order_layered}
-	\end{subfigure}
-	\caption{In all cases, blue lines represent the measured value of
-	the order parameter, black lines are average values calculated from
-	equilibrated Basin B systems at each temperature, green shaded regions
-	represent the standard deviation of each of the black line values, and 
-	red dashed lines show where the temperature is bumped to the next level.
-	(a) The pore spacing decreases smoothly as it approaches Basin B values.
-	(b) Membrane thickness increases steadily with temperature, however
-	it is still far from the Basin B value after 200 ns at 320K. (c) The
-	ratio of pore radius to is uncertainty rapidly decreases initially and
-	approaches the Basin B value smoothly until they finally overlap at 320K.}\label{fig:phase_transition}
-\end{figure}
-
-We varied the relative interlayer orientation between sandwiched and 
-parallel-displaced based on our knowledge of the stability of these two
-pi-stacking modes. Short NVT simulations were run with position restraints
-on aromatic ring carbon atoms. Simulated X-ray diffraction patterns 
-generated from each configuration establish a difference between the two
-stacking modes (Figure~\ref{fig:XRDrestrained}). In each pattern, R-alkanes is present at a distance of
-$\approx 1.5$ \angstrom \textsuperscript{-1}. R-pi is also present in each 
-pattern, although it appears to intersect R-alkanes because the spacing
-between aromatic rings is similar to the alkane chain packing. The difference 
-in aromatic ring spacing between experiment and simulation is likely a result
-of the inability of GAFF to properly handle aromatic interactions. The 
-sandwiched configuration shows R-spots in the expected location. A faint
-reflection is present in the location of R-helix. The parallel
-displaced configuration contains two lines of high intensity with maximum
-intensity occurring where they intersect the alkane chain region due to
-constructive interference between the two features. The lines are located
-where one would expect to see R-helix and, perhaps coincidentally, the 
-intersection with R-alkanes occurs where one would expect to see R-spots.
-As the simulation is progressed, the full line begins to fade 
-(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
-where R-helix exists.
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{0.475\textwidth}
-		\hspace{-1.2cm}
-		\centering
-		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
-		\caption{}\label{fig:rzplayeredrestrained}
-	\end{subfigure}
-	\begin{subfigure}{0.475\textwidth}
-		\hspace{-1.2cm}
-		\centering
-		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
-		\caption{}\label{fig:rzoffsetrestrained}
-	\end{subfigure}
-	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
-	with restraints placed on aromatic carbons shows all major features
-	present in experimental WAXS. Near solid lines at constant z are a result of 
-	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
-	restrained parallel displaced configuration may also contain all
-	major experimental WAXS features. One can argue that R-spots is not present
-	but it is difficult to distinguish because of its intersection with the solid
-	R-helix line. Longer simulations are necessary to determine which structure
-	is the best match to experiment}\label{fig:XRDrestrained}
-\end{figure}
-
-Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-patterns produced from equilibrated MD trajectories shows the most consistency
-with the sandwiched configuration in Basin A. Systems were built in both the 
-parallel displaced and sandwiched configurations with an intial layer spacing of
-3.7 \angstrom. A third system was created by stacking layers in the sandwiched 
-configuration 5 \angstrom apart in order to guide it towards Basin B. For ease of
-reference, the third system will be referred to as the disordered system. The 
-three systems were equilibrated according to our procedure with NPT simulations of 
-greater than 400 ns. Simulated diffration patterns were generated using 
-portions of the trajectory after equilibration. Equilibration was detected
-when the distance between pores and the membrane thickness stopped changing.
-Simulated diffraction patterns for all three structures are shown in 
-Figure ~\ref{fig:XRDsim}. The equilibrated parallel displaced structure exhibits 
-R-alkanes and R-pores in the expected locations. Due to low resolution, making
-out the individual spots of R-pores is challenging and can be validated upon
-full spherical integration of the 3D structure factor. However, the same information
-can be extracted by measuring the pore spacing as described earlier. R-pi is
-also present, intersecting R-alkanes at a lower q value than in experiment.
-The rings prefer to stack $\approx 4.1 \angstrom$ apart as opposed to 3.7 \angstrom.
-R-helix and R-spots are also both missing. The line which intersected both of these
-features in the restrained simulations faded upon equilibration which suggests
-that monomers in the parallel-displaced configuration may not give rise to the 
-experimental WAXS pattern seen. Simulated XRD of the sandwiched configuration 
-contains all features except for R-helix. Most notably, R-spots appears in the
-expected location, which suggests that there is something intrinsic to
-the sandwiched packing that gives rise to such features. Finally, the 
-disordered structure exhibits R-alkanes and R-pores but R-helix, R-pi and R-spots are not
-present. Given the evidence, the sandwiched configuration created with layers spaced
-3.7 \angstrom apart gives rise to an equilibrated structure closest to experiment.
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
-		\caption{}\label{fig:sandwich_rzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{offset_rzplot.png}
-		\caption{}\label{fig:offsetrzplot}
-	\end{subfigure}
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\hspace{-0.9cm}
-		\includegraphics[width=\textwidth]{disorder_rzplot.png}
-		\caption{}\label{fig:disorder_rzplot.png}
-	\end{subfigure}
-	\caption{(a) All major features except R-helix are present in
-	XRD patterns resulting from an equilibrated sandwiched configuration 
-	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
-	(b) All major features execpt R-spots are present in XRD patterns 
-	resulting from an equilibrated parallel displaced configuration in Basin A.
-	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
-	are the only major features present in XRD patterns resulting from an 
-	equilibrated disordered phase}\label{fig:XRDsim}
-\end{figure}
+\graphicspath{{./figures/}}  % put all the figures here
+\maketitle
 
@@
 
-The spots that appear in the simulated XRD pattern of the sandwiched
-conformation are a result of the way alkane tails pack together. Previously,
-the spots in the diffraction pattern had been explained as the product of
-tilted alkane chains. We measured the tilt angle of the alkane chains and 
-showed that our system equilibrates to an average tilt angle close to zero 
-degrees (Figure~\ref{fig:tilt}). To understand the origin of the spots, we 
-determined which atoms gave rise to the feature. By removing atoms from 
-the trajectory and simulating a diffraction pattern, we were able to isolate
-the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the tails are mostly flat, we
-plotted the centroids of the tails and measured the angle between each centroid 
-and its nearest neighbors with respect to the plane of the membrane (Figure~\ref{fig:centroids}). The 
-distribution of these angles is consistent with the location of the spots (Figure~\ref{fig:angle_distribution}).
-We reason that monomer tails stacked closely in the sandwiched conformation
-are forced to splay apart and pack in between in each other which creates a
-nearly hexagonal array of packed tails.
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{ps5layered.png}
+		\caption{}\label(fig:ps5layered}
+	\end{subfigure}
+	\begin{subfigure}
+		\centering
+		\includegraphics[width=\textwidth]{ps5offset.png}
+		\caption{}\label{fig:ps5offset}
+	\end{subfigure}
+\end{figure}
 
-\begin{figure}[H]
+\begin{figure}[!ht]
         \centering
@@
 
-\subsection*{Ionic conductivity calculation}
-
-The model gives reasonable estimates of ionic conductivity for both phases.
-Calculated values of ionic conductivity obtained using the Nernst Einstein
-relation and Collective Diffusion model are compared in Table~\ref{table:conductivity}.
-The two methods agree with each other within error, although the 
-uncertainty obtained using the Collective Diffusion model is much higher.
-Much longer simulations are needed to lower the uncertainty. This is 
-especially true of the value calculated for Basin B using the collective
-diffusion model. The simulation was only run for 200 ns. Basin A collective
-diffusion calculations were generated from a 500 ns simulation. In both 
-cases, our calculated values would benefit from longer simulations. 
-For this reason we will likely only use the Nernst Einstein relation
-in future calculations of this type. Interestingly, Basin B 
-has a higher ionic conductivity than Basin A. Conductivity is enhanced in
-Basin B due to a higher sodium ion diffusivity. Transport of sodium is
-likely facilitated by the homogeneity of Basin B. Sodium ions have less
-sites to move to in Basin A. Currently there is no experimental
-evidence of this trend, but it may be the subject of a future study. 
-In both cases, our calculated values for Basin A are higher than the 
-experimental values, as expected. Some of the discrepancy is likely a result
-of using an imperfect forcefield. However, the real system, although mostly
-aligned and straight, has a distribution of azimuthal angles, meaning 
-that the pores have a degree of tortuosity which lowers the effective 
-ionic conductivity of the bulk membrane. The ordering from isotropic to
-mostly aligned mesophases showed an 85 fold increase in ionic conductivity.
-We would expect additional gains in a perfect system.
-
-\begin{table}
-\centering
-\begin{tabular}{ccc}
-\toprule
-\multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
-\hline
-Method & Basin A & Basin B \\
-\midrule
-Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
-Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
-Experiment & \num{1.33e-5} (0.10) & -- \\
-\bottomrule
-\end{tabular}
-\caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
-agree within error. Both methods give calculated values of ionic conductivity which
-are an order of magnitude higher than experimental values~\label{table:conductivity}}.
-\end{table}
-
-\subsection*{Implementation of the crosslinking algorithm}
-
-We applied the crosslinking algorithm to an equilibrated structure in Basin B.
-The procedure will be repeated with Basin A in the near future.
-The resulting crosslinked structure has an even distribution of
-crosslinks between monomer tails of the same monomer, monomers stacked on  % table of values here
-top of each other and monomers in other pores, including across periodic
-boundaries. The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
-constant under a range of simulation conditions. Figure~\ref{fig:xlink} compares
-the pore behavior of a system that was a crosslinked and simulated for 10 ns to 
-the pore behavior of the same system taken just before crosslinking and run for 10 ns.
-Rather than plotting an average pore spacing, each pore-to-pore distance is plotted
-separately. Visually, one can tell that the crosslinked pores are locked in place. 
-The smaller pore spacing is also apparent by comparing the two plots. 
-The simulations discussed previously have not been crosslinked. Moving forward,
-the sandwiched system will be crosslinked in Basin A and used for
-transport studies.
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
-		\caption{}\label{fig:p2p_diagram}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
-		\caption{}\label{fig:no_xlink_p2p}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{xlink_p2p.png}
-		\caption{}\label{fig:xlink_p2p}
-	\end{subfigure}
-	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
-	Each numbered circle represents a pore. Distances are measured along each of the 
-	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
-	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
-	individual pores in the crosslinked system are stable relative to the uncrosslinked
-	system}\label{fig:xlink}
-\end{figure}
+\end{document}

### 2017-11-08 Ben_Manuscripts/structure_paper/Outline.tex
Equilibration scheme for bcc phase system. Should work on bridges
New figures and updates to outline

@@
     \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
-    the monomer named Na-GA3C11 has been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
+    the monomer named Na-GA3C11 have been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
     zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
+    % BJC: New paragraph?
     \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
-    aligned, resulting in a low flux membrane, slowing research in the field.
+    aligned, resulting in low flux membranes, slowing research in the field.
     \item In 2014, Feng et al. showed that the mesophases could be aligned 
@@
     \item Following this breakthrough, research into LLC membranes has been
-    reinvigorated
-  \end{itemize}
+    reinvigorated.
+  \end{itemize}
+
+  % BJC: Not sure this figure needs to be in the paper
+  \begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{soft_confinement.png}
+	\caption{The wedge shaped liquid crystal monomer (a) self assembles into 
+	mesophases with hexagonally packed pores (b). The pores are made of 
+	stacked monomer disks. A sub-micron-thick film is created by casting a 
+	dilute solution of Na-GA3C11/THF solution onto a silicon substrate and 
+	and allowing the solvent to evaporate. The thin film contains nanoporous 
+	columns which lie parallel to the film plane. (d) When a soft PDMS pad is 
+	imposed to the thin film, with subsequent thermal annealing, the columns
+	align perpendicular to the film plane. (e) Photo-cross-linking of the
+	aligned film creates a mechanically stable thin film with vertically 
+	aligned nanopores}~\label{fig:soft}
+  \end{figure}
 
@@
     a laboratory setting without a robust model.
-    \item The only source of predictive modeling has been macroscopic models 
+    \item The only source of predictive modeling for LLC systems have been macroscopic models 
     which likely do not adequately describe transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
@@
   \end{itemize}
+
+  %BJC: Figure here showing previous level of detail compared to atomistic level of detail
+  \begin{figure}[ht]
+  \centering
+	\begin{subfigure}{0.45\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
+		\caption{}~\label{fig:undetailed_pore}
+	\end{subfigure}
+	\begin{subfigure}{0.45\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{nanopore.png}
+		\caption{}~\label{fig:detailed_pore}
+	\end{subfigure}
+  \caption{(a) Our previous understanding of the pore structure allows us to speculate
+	   about separation behavior. (b) A detailed molecular model will allow us to
+	   directly observe solute transport}~\label{fig:detail}
+  \end{figure}
 
@@
 	\item We can use simulated X-ray diffraction patterns to see if there is
-        any meaningful structural difference between a dry and "wet" system
+        any meaningful structural difference between a "dry" and "wet" system
    \end{itemize}
@@
     \item Simulations of greater than 100 ns show no indicators of progress 
-    towards an ordered system.  %BJC: include more details in supplment?
+    towards an ordered system.  %BJC: include more details in supplment
     \item To bypass the slow self-assembly process, python scripts are used
@@
         explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: References
-        \item The first corresponds to the spacing and symmetry of
+        \item The final feature corresponds to the spacing and symmetry of
         the d\textsubscript{100} plane which can be related to the distance between
@@
                 \raisebox{.2\textwidth}{%
-                \includegraphics[width=\linewidth]{WAXS_soft_confined.png}
+                \includegraphics[width=\linewidth]{WAXS_annotated.png}
                 }
@@
         \end{subfigure}
-        \caption{(a) 2D wide angle X-ray scattering gives details about repeating
-        features less than 1 nanometer apart. (b) 1D small angle X-ray scattering
-        indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
+        \caption{(a) 1D small angle X-ray scattering indicates hexagonal packing of
+	pores as well as the spacing between pores (b) 2D wide angle X-ray scattering 
+	gives details about repeating features less than 1 nanometer apart}\label{fig:SWAXS}
   \end{figure}
@@
     head group as a reference atom, and placed it a distance r from the pore center,
-    where r is the pore radius. (See Supplemental Information) %BJC: figure making that clear
+    where r is the pore radius (~\ref{fig:pore_radius_illustration}). % BJC: Figure in Supplemental Information?
     \item We will not make direct comparisons of pore radius between our model 
@@
   \end{itemize}
+
+  \begin{figure}[ht]
+ 	\centering
+ 	\includegraphics[width=\textwidth]{pore_radius_illustration.png}
+	\caption{The pore radius of the initial configuration is defined using the 
+        carboxylate carbon as a reference}~\label{fig:pore_radius_illustration}
+  \end{figure}
 
@@
           slowly released until there is no more restraining potential.
-          \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-          ensemble for at least 400 ns.
+          \item The resulting unrestrained structure is allowed to equilibrate for 5 ns 
+	  in the NPT ensemble with pressure controlled by the berendsen barostat.
+	  \item Long, NPT equilibration simulations are run for at least 400 ns using the 
+          Parrinello-Rahman barostat with a time consant of 10 ps.
       \end{itemize}
@@
           %\item We obtained an estimate of equilibrium pore water content by solvating
-          %an initial configuration with water baths above and below the membrane. 
+          % an initial configuration with water baths above and below the membrane. 
 	  %\item We ran the solvated system according to Scheme A but with a 1000 ns equilibration
@@
     \item Ion concentration was measured with respect to the entire unit cell. 
+    % new paragraph
     \item The second method, termed the 'Collective Diffusion' model, measures 
@@
   \begin{itemize}
-        \item Both the sandwiched and parallel displaced configurations were tested.
-        \item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
-        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
-        %BJC: Working on getting them all run out to 400 ns
+        \item We created systems in both the parallel displaced and sandwiched configurations
+	\item All systems were prepared according to the dry equilibration procedure
+        \item All systems are stable after 400 ns of simulation.  
         \item Table ~\ref{table:p2p} shows the pore spacing for all systems tested.
@@
 
+  %BJC: maybe split into 2 paragraphs
   To answer (2), we verified that the system stays partitioned into layers by
-  plotting the pair correlation function, $g(z)$ calculated between aromatic rings along
+  plotting the pair correlation function, $g(z)$ calculated between atoms along
   the length of the pores (Fig~\ref{fig:zdf}).
   \begin{itemize}
-        \item Sandwiched configuration layers stack 4.29 \angstrom apart while
-        parallel displaced configuration layers stack 4.37 \angstrom apart.
-        The power spectrums used to calculate the reported layer spacing are given in the 
-        Supplemental Information.  %BJC: "Power spectrum" and okay description here?
+	\item We measured $g(z)$ with respect to aromatic rings in the head groups
+	and, separately, with respect to carbon atoms on the alkane chains.
+	\item In both cases, we see a degree of layer partitioning
+        \item Using the head groups as reference, we see that sandwiched configuration
+	layers stack 4.29 \angstrom apart while parallel displaced configuration layers
+	stack 4.37 \angstrom apart.
+	\item Using the alkane chain carbons as reference we see a layer spacing of 4.39 \angstrom
+	and 4.38 \angstrom in the sandwiched and parallel displaced configurations respectively.
+        \item The power spectrums used to calculate the reported layer spacings are given in the 
+        Supplemental Information.  %BJC: "Power spectrum" an okay description here?
+	\item We see a difference in the spacing in the head group versus tail region
+	because there is more volume to fill with less densely packed carbon chains in the tail region. 
+	% BJC: vvv Need to get the same information for the tail zdfs.
 	\item Even though the layer spacing is similar, the sandwiched configuration
@@
   \midrule
-  4 & $3.71 \pm 0.04$ & $3.84 \pm 0.02$ \\
+  4 & $3.72 \pm 0.04$ & $3.84 \pm 0.02$ \\  % done
   5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
-  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
-  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
-  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
+  6 & $4.69 \pm 0.04$ & $4.72 \pm 0.03$ \\
+  7 & $4.66 \pm 0.02$ & $4.82 \pm 0.03$ \\  % done
+  8 & $5.00 \pm 0.04$ & $5.33 \pm 0.02$ \\
   \bottomrule
@@
   \begin{itemize}
-	\item We created configurations in both the parallel displaced and sandwiched
-	configurations
-        \item The systems were assembled and equilibrated according to our dry equilibration procedure
-        \item Simulated diffration patterns were generated using portions of the
+	\item Systems of 5 monomers per layer in the parallel displaced and sandwiched
+	configurations were tested.
+        \item Simulated patterns were generated using portions of simulation
         trajectory after equilibration.
-        \item We assume the simulation has equilibrated when the distance between
-        pores and the membrane thickness stopped changing. %BJC: might be better placed in methods
-        \item Simulated diffraction patterns for both structures are shown and 
-	compared to experimenta in Figure ~\ref{fig:XRDsim}.
+        \item The patterns for both structures are shown and compared to experiment
+	in Figure ~\ref{fig:XRDsim}.
   \end{itemize}
@@
 
-  \begin{figure}[ht]
-  \begin{subfigure}{.83\linewidth}
-        \centering
-        \begin{subfigure}{0.4\linewidth}
-                \centering
-                \includegraphics[width=\linewidth, trim={2.5cm 0 4cm 2cm}, clip]{WAXS_raw.png}%
+%  \begin{figure}[ht]
+%  \begin{subfigure}{.83\linewidth}
+%        \centering
+%        \begin{subfigure}{0.4\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth, trim={2.5cm 0 4cm 2cm}, clip]{WAXS_raw.png}%
+%                \caption{}~\label{fig:raw_waxs}
+%        \end{subfigure}%
+%        \begin{subfigure}{0.4\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_offset.png}
+%                \caption{}~\label{fig:rz_offset}
+%        \end{subfigure}
+%        \begin{subfigure}{0.4\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_layered.png}
+%                \caption{}~\label{fig:rz_layered}
+%        \end{subfigure}%
+%        \begin{subfigure}{0.4\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_disordered.png}
+%                \caption{}~\label{fig:rz_disordered}
+%        \end{subfigure}
+%  \end{subfigure}%
+%  \begin{subfigure}{0.14\linewidth}
+%        \centering
+%        \vspace{-1cm}
+%        \includegraphics[width=\linewidth]{colorbar_jet.png}
+%  \end{subfigure}
+%  \caption{(a) Experimental 2D WAXS data contains 5 major reflections which we aim to match. The remaining
+%  three images are diffraction patterns simulated from MD trajectories. (b) The parallel displaced
+%  configuration gives rise to all reflections of interest. (c) The sandwiched configurations gives rise to a
+%  pattern with all major reflections except R-helix. R-spots is strong relative to R-alkanes in comparison
+%  to the parallel displaced configuration. (d) The disordered pore configuration creates a pattern with only
+%  R-alkanes and R-pores in common with experiment}~\label{fig:xrd}
+%  \end{figure}
+
+  \begin{figure}
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+        \vspace{-0.2em}
+        \includegraphics[width=1.018\linewidth]{layered_rzplot.png}
+        \caption{}~\label{fig:rz_layered}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+        \vspace{0.25em}
+        \includegraphics[scale=0.0987]{WAXS_raw.png}
         \caption{}~\label{fig:raw_waxs}
-        \end{subfigure}%
-        \begin{subfigure}{0.4\linewidth}
-                \centering
-                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_offset.png}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{offset_rzplot.png}
         \caption{}~\label{fig:rz_offset}
   \end{subfigure}
-        \begin{subfigure}{0.4\linewidth}
-                \centering
-                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_layered.png}
-                \caption{}~\label{fig:rz_layered}
-        \end{subfigure}%
-        \begin{subfigure}{0.4\linewidth}
-                \centering
-                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_disordered.png}
-                \caption{}~\label{fig:rz_disordered}
-        \end{subfigure}
-  \end{subfigure}%
-  \begin{subfigure}{0.14\linewidth}
-        \centering
-        \vspace{-1cm}
+  \begin{subfigure}{0.0544\linewidth}
+        \centering
+        \vspace{-3.30em}
         \includegraphics[width=\linewidth]{colorbar_jet.png}
   \end{subfigure}
-  \caption{(a) Experimental 2D WAXS data contains 5 major reflections which we aim to match. The remaining
-  three images are diffraction patterns simulated from MD trajectories. (b) The parallel displaced
-  configuration gives rise to all reflections of interest. (c) The sandwiched configurations gives rise to a
-  pattern with all major reflections except R-helix. R-spots is strong relative to R-alkanes in comparison
-  to the parallel displaced configuration. (d) The disordered pore configuration creates a pattern with only
-  R-alkanes and R-pores in common with experiment}~\label{fig:xrd}
+  \caption{The simulated X-ray diffraction patterns for simulations run in the
+  sandwiched (a) and parallel-displaced (c) configurations are compared to experiment (b). 
+  The parallel displaced configuration is the only one that exhibits all major
+  reflections of interest to some degree}
   \end{figure}
@@
   	\item Previously, the spots in the diffraction pattern had been explained 
-	as the product of tilted alkane chains. % BJC: reference
+	as the product of tilted alkane chains. % BJC: reference 2014 ACS nano paper
 	\item We measured the tilt angle of the alkane chains and showed that our 
-	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
+	system equilibrates to an average tilt angle close to zero degrees ~\ref{fig:tilt} % Could belong in supplemental. Leaving here for now 
 	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
@@
 
-  The peaks in the tail angle distribution are consistent with the location of R-spots.
+  \begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
+  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
+  indicates an average tilt angle near 7\degree which is far from the 37\degree tilt angle 
+  previously used to explain R-spots}~\label{fig:tilt}
+  \end{figure}
+
+  The peaks in the tilt angle distribution are consistent with the location of R-spots.
   \begin{itemize}
@@
 	\item We do not have an experimental measurement of water in the pores
-	\item We decided the number of waters to put in each pore by estimating
-        the number of hydrogen bonds in which pore entities could participate.
-	\item In solution, each headgroup has a charge of -1
-	\item We estimate there to be about 4 water molecules per layer based 
-	on various packing configurations and geometric constraints
-	\item 4 water molecules per layer translates to about 1.6 wt \%
+	\item We tested a range of water concentrations from 0.5 to 5 percent % working on a 0.5 wt % sytstem now just to see
+	\item Our lower bound represents a system with on average 2 water 
+	molecules for each monomer layer.
+	\item Figure ~\ref{fig:solvation} shows results for each configuration.
+%	\item Initially, we decided the number of waters to put in each pore by
+%	estimating the number of hydrogen bonds in which pore entities could participate.
+%	\item In solution, each headgroup has a charge of -1
+%	\item We estimate there to be at least 2 water molecules per layer based 
+%	on various packing configurations and geometric constraints
+%	\item 4 water molecules per layer translates to about 1.6 wt \%
+  \end{itemize}
+
+  \begin{figure}[ht]
+	\centering
+	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
+	\label{fig:solvation}
+  \end{figure}
+
+  In all cases, water disrupts structuring of the model.
+  \begin{itemize}
+	\item The plots in Figure ~\ref{fig:solvation} are normalized 
+	to have the same colorbar as the dry systems. 
+	\item The intensity of the reflections decrease when water is 
+	added to the system.
+	\item In systems built with 5 weight percent water, R-$\pi$ and
+	R-spots become nearly indistinguishable from R-alkanes.
+  \end{itemize}
+
+  Water is not needed to obtain and simulate the correct equilibrium 
+  membrane structure.
+  \begin{itemize}
+	\item We note that water absorbed during membrane synthesis may
+        be present in far lower concentrations than those 
+        tested here.
+	\item We do not eliminate the possibility that water is necessary
+        in order to drive self-assembly. Studying the mechanisms of self assembly is
+	beyond the scope of this work.
+	\item However, once the system has formed the Col\textsubscript{h} 
+	phase, adding water only creates disorder in the structure
+	\item In the equilibrium configuration, if water exists, it is confined
+	to the pore region where there is no driving force for aggregation of 
+	water molecules. 
+	\item The packing of water molecules will be too sparse to form a 
+	hydrogen bonding network.
   \end{itemize}
@@
 
-  We use the equilibrated offset system in the OP basin to calculate ionic 
+  We use the equilibrated parallel displaced system to calculate ionic 
   conductivity since its structure is the closest match to experiment.
@@
 	Einstein relation and Collective Diffusion model are compared in 
-	Table~\ref{table:conductivity}.
+	Figure~\ref{fig:conductivity}.
 	\item The two methods agree with each other within error, although the 
 	uncertainty obtained using the Collective Diffusion model is much higher.
-	\item Much longer simulations are needed to lower the uncertainty. % TODO: Run Basin B out longer at same conditions as A
-	\item Collective diffusion calculations were generated from 
-	500 ns simulations.
-	\item Our calculated values would benefit from longer simulations. 
+	\item Much longer simulations are needed to lower the uncertainty, however it
+	is unfeasible to do so with large model. 
 	\item For this reason we will likely only use the Nernst Einstein relation
@@
 
-  The CP basin has a higher ionic conductivity than the OP basin.
-  \begin{itemize}
-	\item We hypothesize that conductivity is enhanced in Basin B due to a 
-	higher sodium ion diffusivity.
-	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
-	Sodium ions have less nearby sites to move to in Basin A.
-	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
-	\item In both cases, our calculated values for Basin A are higher than the 
-	experimental values, as expected. 
-	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
-	\item However, the real system, although mostly aligned and straight, has a 
-	distribution of azimuthal angles, meaning that the pores have a degree of 
-	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
-	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
-	fold increase in ionic conductivity. We would expect additional gains in a 
-	perfectly aligned system.
-  \end{itemize}
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
-  \hline
-  Method & Basin A & Basin B \\
-  \midrule
-  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
-  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
-  Experiment & \num{1.33e-5} (0.10) & -- \\
-  \bottomrule
-  \end{tabular}
-  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
-  agree within error. Both methods give calculated values of ionic conductivity which
-  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
-  \end{table}
+  The calculated values of ionic conductivity are higher than experiment by an
+  order of magnitude. 
+  \begin{itemize}
+	\item One can justify the reason for this result by considering the 
+	real system studied experimentally
+	\item The ionic conductivity measurement to which we are comparing was done
+	on a \SI{80}{\micro\metre} thick film, nearly 10,000 times thicker than 
+        our simulated system. 
+	\item The thick film likely has defects leading to non-continuous pores and
+	imperfect alignment.
+	\item The 2D SAXS pattern highlights the small degree of tortuosity present
+	in the system  % BJC: insert 2D SAXS data -- maybe azimuthal distribution
+	\item It has been shown that there is a large dependence of Ionic conductivity
+	on the alignment of the pores
+	\item The ionic conductivity of an unaligned film is 85 times lower than that
+	of a nearly aligned film referenced here  % BJC: reproduce figure from 2014
+	\item It is not unreasonable that a thin, perfectly aligned film would have 
+	a value of ionic conductivity in agreement with our model
+  \end{itemize}
+
+%  The CP basin has a higher ionic conductivity than the OP basin.
+%  \begin{itemize}
+%	\item We hypothesize that conductivity is enhanced in Basin B due to a 
+%	higher sodium ion diffusivity.
+%	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
+%	Sodium ions have less nearby sites to move to in Basin A.
+%	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
+%	\item In both cases, our calculated values for Basin A are higher than the 
+%	experimental values, as expected. 
+%	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
+%	\item However, the real system, although mostly aligned and straight, has a 
+%	distribution of azimuthal angles, meaning that the pores have a degree of 
+%	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
+%	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
+%	fold increase in ionic conductivity. We would expect additional gains in a 
+%	perfectly aligned system.
+%  \end{itemize}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\linewidth]{IC_offset.png}
+	\caption{Calculated ionic conductivity using the Nernst-Einstein relation
+	and Collective Diffusion model agree with error. Both methods give calculated
+	values of ionic conductivity an order of magnitude higher than the experimental
+	value}
+	\label{fig:conductivity}
+\end{figure}
+
+%BJC: vvv replaced by bar plot above
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{ccc}
+%  \toprule
+%  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
+%  \hline
+%  Method & Basin A & Basin B \\
+%  \midrule
+%  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
+%  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
+%  Experiment & \num{1.33e-5} (0.10) & -- \\
+%  \bottomrule
+%  \end{tabular}
+%  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
+%  agree within error. Both methods give calculated values of ionic conductivity which
+%  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
+%  \end{table}
 

### 2017-11-08 BCC/Scripts/bcc_equil.sh

@@ -32,19 +32,20 @@ while getopts "b:p:d:r:n:I:w:S:T:R:c:P" opt; do
     esac
 done
 
-#if [[ ${cluster} -eq 1 ]]; then
-#    GMX="mpirun -np ${NP} gmx_mpi"
-#else
-#    GMX="gmx"
-#fi
-#
-#bcc_build.py -b ${build_mon}.gro -p ${phase} -d ${dimension} -dens ${density} -shift ${SHIFT} -o initial.gro -wt ${wt_percent} -sol ${solvent}
-#reorder_gro.py -i initial.gro -o bcc.gro -I ${ion}
-#echo "Initial unit cell built"
-#input.py --bcc -b ${build_mon} -s 5000 # only care about em.mdp and topol.top at this step
-#
-## really spread the monomers apart
-#scale.py -g bcc.gro -o bcc.gro -f 2  # triple each dimension of the unit cell and isotropically scale all head group positions
+if [[ ${cluster} -eq 1 ]]; then
+    GMX="mpirun -np ${NP} gmx_mpi"
+else
+    GMX="gmx"
+fi
+
+bcc_build.py -b ${build_mon}.gro -p ${phase} -d ${dimension} -dens ${density} -shift ${SHIFT} -o initial.gro -wt ${wt_percent} -sol ${solvent}
+reorder_gro.py -i initial.gro -o bcc.gro -I ${ion}
+echo "Initial unit cell built"
+input.py --bcc -b ${build_mon} -s 5000 # only care about em.mdp and topol.top at this step
+
+# really spread the monomers apart
+scale.py -g bcc.gro -o bcc.gro -f 2  # triple each dimension of the unit cell and isotropically scale all head group positions
+exit
 #gmx grompp -f em.mdp -p topol.top -c bcc.gro -o em
 #${GMX} mdrun -v -deffnm em
 #

### 2017-11-08 HII/Scripts/xlink.sh

@@ -2,7 +2,7 @@
 set -e
 # A script to iteratively crosslink a LLC system
 
-CUTOFF=5  # percent of distribution that will be labeled close enough to bond
+CUTOFF=2.5  # percent of distribution that will be labeled close enough to bond
 TERM_PROB=5  # probability of termination of carbons meeting bonding criteria
 GRO='wiggle.gro'  # initial .gro file to be crosslinked
 CUTOFF_RAD=20  # percent of distribution that are labeled close enough to bond in the context of reactive radicals
@@ -87,7 +87,7 @@ find ${TOP} -type f -exec sed -i 's/crosslinked_new.itp/crosslinked.itp/g' {} \;
 
 gmx grompp -f em.mdp -p ${TOP} -c wiggle_no_dummies.gro -o em
 gmx mdrun -v -deffnm em
-gmx grompp -f ${NPT} -p ${TOP} -c em.gro -o wiggle
+gmx grompp -f npt.mdp -p ${TOP} -c em.gro -o wiggle
 gmx mdrun -v -deffnm wiggle
 
 mail -s "Crosslinking Done" -a xlink.log benjamin.coscia@colorado.edu <<< "The crosslinking has terminated, woo!"

### 2017-11-10 Ben_Manuscripts/structure_paper/Outline.tex
New figures and more revision

@@
   %BJC: Figure here showing previous level of detail compared to atomistic level of detail
-  \begin{figure}[ht]
+  \begin{figure}
   \centering
@@
 		\centering
-		\includegraphics[width=\textwidth]{nanopore.png}
+		\includegraphics[width=\textwidth]{detailed_pore.png}
 		\caption{}~\label{fig:detailed_pore}
@@
    (4) Is it necessary to include any water in order to appropriately model the 
-   Col\testsubscript{h} phase?
+   Col\textsubscript{h} phase?
    \begin{itemize}
@@
 
-  \begin{figure}[!ht]
+  \begin{figure}
 	\centering
@@
 
-  \begin{figure}[!ht]
+  \begin{figure}
         \centering
@@
 
-  \begin{figure}[ht]
+  \begin{figure}
  	\centering
@@
         \item All systems are stable after 400 ns of simulation.  
-        \item Table ~\ref{table:p2p} shows the pore spacing for all systems tested.
+        \item Table ~\ref{fig:p2p} shows the pore spacing for all systems tested.
         \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
@@
 
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  		   & \multicolumn{2}{c}{Starting Configuration} \\
-  \hline
-  Monomers per layer & Sandwiched & Parallel Displaced \\
-  \midrule
-  4 & $3.72 \pm 0.04$ & $3.84 \pm 0.02$ \\  % done
-  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
-  6 & $4.69 \pm 0.04$ & $4.72 \pm 0.03$ \\
-  7 & $4.66 \pm 0.02$ & $4.82 \pm 0.03$ \\  % done
-  8 & $5.00 \pm 0.04$ & $5.33 \pm 0.02$ \\
-  \bottomrule
-  \end{tabular}
+  \begin{figure}
+	\centering
+	\includegraphics[width=0.5\linewidth]{p2p.png}
 	\caption{The pore spacing (given in nm) of the model increases as
@@
 	per layer in a parallel displaced configuration result in a pore spacing
-  closest to the experimental 4.12 nm}
-  \label{table:p2p} 
-  \end{table}
+	closest to the experimental 4.12 nm}~\label{fig:p2p}
+  \end{figure}
+
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{ccc}
+%  \toprule
+%  		   & \multicolumn{2}{c}{Starting Configuration} \\
+%  \hline
+%  Monomers per layer & Sandwiched & Parallel Displaced \\
+%  \midrule
+%  4 & $3.72 \pm 0.04$ & $3.84 \pm 0.02$ \\  % done
+%  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
+%  6 & $4.69 \pm 0.04$ & $4.72 \pm 0.03$ \\
+%  7 & $4.66 \pm 0.02$ & $4.82 \pm 0.03$ \\  % done
+%  8 & $5.00 \pm 0.04$ & $5.33 \pm 0.02$ \\
+%  \bottomrule
+%  \end{tabular}
+%  \caption{The pore spacing (given in nm) of the model increases as
+%  number of monomers in each layer increases. The pore spacing of a system
+%  starting in the sandwiched configuration is systematically lower than 
+%  that started in an offset configuration. Systems built with 5 monomers
+%  per layer in a parallel displaced configuration result in a pore spacing
+%  closest to the experimental 4.12 nm}
+%  \label{table:p2p} 
+%  \end{table}
 
@@
 
-  \begin{figure}[ht]
+  \begin{figure}
   \centering
@@
 
-  \begin{figure}[ht]
+  \begin{figure}
 	\centering
@@
         our simulated system. 
-	\item The thick film likely has defects leading to non-continuous pores and
+	\item The thick film likely has defects leading to non-contiguous pores and
 	imperfect alignment.
-	\item The 2D SAXS pattern highlights the small degree of tortuosity present
-	in the system  % BJC: insert 2D SAXS data -- maybe azimuthal distribution
+	\item The 2D SAXS pattern shows the small degree of tortuosity present
+	in the system (~\ref{fig:2DSAXS})  % BJC: insert 2D SAXS data -- maybe azimuthal distribution
 	\item It has been shown that there is a large dependence of Ionic conductivity
@@
   \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{2D-SAXS_cropped.png}
+  % BJC: I will add axes with q values if this ends up in the final draft
+  % BJC: I'll also see what I can do about all the white speckles
+  \caption{The experimental two dimensional SAXS pattern exhibits reflections
+  resulting from highly aligned pore regions. A perfectly aligned system 
+  would exhibit sharp dots at the same locations of the refelctions shown. 
+  An isotropically aligned system the refelctions would appear as 
+  rings centered about the origin}~\label{fig:2DSAXS}
+  \end{figure}
+
+\begin{figure}
+        \centering
+        \includegraphics[width=0.5\linewidth]{IC_offset.png}
+        \caption{Calculated ionic conductivity using the Nernst-Einstein relation
+        and Collective Diffusion model agree with error. Both methods give calculated
+        values of ionic conductivity an order of magnitude higher than the experimental
+        value}
+        \label{fig:conductivity}
+\end{figure}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\linewidth]{IC_offset.png}
-	\caption{Calculated ionic conductivity using the Nernst-Einstein relation
-	and Collective Diffusion model agree with error. Both methods give calculated
-	values of ionic conductivity an order of magnitude higher than the experimental
-	value}
-	\label{fig:conductivity}
-\end{figure}
-
 %BJC: vvv replaced by bar plot above
@@
 
-  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
-  the OP basin.
+  We applied the crosslinking algorithm to the equilibrated parallel-displaced  
+  configuration with 5 monomers per layer.
   \begin{itemize}  %BJC: working on the following. The following is what I expect
@@
 	between monomers in the same pore and between monomers in different pores 
-	including periodic boundaries.
-	\item We reach 95 \% conversion of terminal vinyl groups
+	including periodic boundaries.  % BJC: might leave this detail in the supplemental
+	\item We reach 95 \% conversion of terminal vinyl groups % BJC: we'll see
 	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
-	crosslinked
-	\item Major features are still present in the X-ray diffraction
-	\item The ionic conductivity is higher/lower in the crosslinked system
-  \end{itemize}
-  %BJC: THe following figure will be replaced with one representative of the new
-  % data I am  collecting above.
-  \begin{figure}[!ht]
-	\centering
-	\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
-		\caption{}\label{fig:p2p_diagram}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
-		\caption{}\label{fig:no_xlink_p2p}
-	\end{subfigure}
-		\begin{subfigure}{0.31\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{xlink_p2p.png}
-		\caption{}\label{fig:xlink_p2p}
-	\end{subfigure}
-	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
-	Each numbered circle represents a pore. Distances are measured along each of the 
-	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
-	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
-	individual pores in the crosslinked system are stable relative to the uncrosslinked
-	system}\label{fig:xlink}
+	crosslinked  % probably smaller
+	\item We simulated the crosslinked simulations in the NPT ensemble for 100 ns
+	\item Major features are still present in the X-ray diffraction ~\ref{fig:rzplot_xlink} % BJC: maybe
+	\item The ionic conductivity is higher/lower in the crosslinked system ~\ref{fig:ic_xlink} % BJC: Nernst-Einstein is lower. Need a longer simulation to check Collective-Diffusion 
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[widht=\textwidth]{rzplot_xlink.png}
+	\caption{}~\label{fig:rzplot_xlink}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{ic_xlink.png}
+	\caption{}~\label{fig:ic_xlink}
+  \end{subfigure}
+  \caption{(a) Reflections produced by the crosslinked configuration fade relative
+  to the uncrosslinked system. The colorbar shown is the same used for the uncrosslinked
+  system. (b) The ionic conductivity is smaller relative to the uncrosslinked system, but
+  still much larger than the experimental value}~\label{fig:xlink}
   \end{figure}
+
+%  \begin{figure}
+%	\centering
+%	\begin{subfigure}{0.31\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
+%		\caption{}\label{fig:p2p_diagram}
+%	\end{subfigure}
+%		\begin{subfigure}{0.31\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
+%		\caption{}\label{fig:no_xlink_p2p}
+%	\end{subfigure}
+%		\begin{subfigure}{0.31\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{xlink_p2p.png}
+%		\caption{}\label{fig:xlink_p2p}
+%	\end{subfigure}
+%	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
+%	Each numbered circle represents a pore. Distances are measured along each of the 
+%	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
+%	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
+%	individual pores in the crosslinked system are stable relative to the uncrosslinked
+%	system}\label{fig:xlink}
+%  \end{figure}
 
@@
 	attempt to examine their structure with the same level of detail presented here.
+	\item We were able to deduce that layers are composed of 5 monomers 
         \item We have confirmed that monomers stay partitioned in layers.
-	\item We were able to deduce that layers are composed of 5 monomers.
-	\item We have identified two metastable basins which each consist of a set of 
-	similar monomer configurations characterized by the degree of order in the pore region.
-	\item We verified that the basins are not separate phases.
 	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
@@
 	\item Simulated diffration patterns generated from MD trajectories suggest that
-	the offset configuration produces a structure with the closest match to experiment. 
-	\item Even though our model only answers these questions for a system created by 
-	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
-	little extra effort. 
+	the parallel-displaced configuration produces a structure with the closest match to experiment.
+	\item Finally, water is not needed to maintain membrane structure 
+	\item Now that we have a good idea of what the membrane structure should look like, we will
+	evaluate transport of various solutes within the system. 
+	\item We will apply the knowledge gained from this study in order to 
+        suggest improvements to the existing system as well as to evaluate new
+	unsynthesized LLC systems.
+%	\item Even though our model only answers these questions for a system created by 
+%	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
+%	little extra effort. 
   \end{itemize}

### 2017-11-10 HII/Scripts/xlink.sh

@@ -18,8 +18,9 @@ TOP='topol.top'
 MDP='npt.mdp'
 INIT_CONFIG='initial.gro'
 TIMESTEP=0.001
+EMSTEPS=5000
 
-while getopts "c:t:g:d:s:x:f:m:C:p:M:i:S:" opt; do
+while getopts "c:t:g:d:s:x:f:m:C:p:M:i:S:E:" opt; do
     case $opt in
     c) CUTOFF=$OPTARG;;
     t) TERM_PROB=$OPTARG;;
@@ -34,6 +35,7 @@ while getopts "c:t:g:d:s:x:f:m:C:p:M:i:S:" opt; do
     M) MDP=$OPTARG;;
     i) INIT_CONFIG=$OPTARG;;
     S) TIMESTEP=$OPTARG;;
+    E) EMSTEPS=$OPTARG;;
     esac
 done
 
@@ -45,7 +47,7 @@ if [ ${ITERATION} != 0 ]; then
     ITERATION=$((ITERATION+1))
 fi
 
-input.py -b ${MONOMER} -c ${GRO} -x -l ${SIM_LENGTH} -f ${FRAMES} --genvel yes -d ${TIMESTEP}
+input.py -b ${MONOMER} -c ${GRO} -x -l ${SIM_LENGTH} -f ${FRAMES} --genvel yes -d ${TIMESTEP} -s ${EMSTEPS}
 
 while [ ${STOP} -eq 0 ]; do
     if [ ${ITERATION} == 0 ]; then

### 2017-11-22 Ben_Manuscripts/structure_paper/Outline.tex
Added bibtex file and compiled pdf
updates to outline and debugging

@@
 	tails and measured the angle between each centroid and its nearest neighbors
-	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
+	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).  %BJC: at one point Matt mention doing a correlation function instead of just measuring the angles
 	\item We see distinct peaks in the distribution of these angles (Figure~\ref{fig:tail_packing})
@@
 	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
-	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
-	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
-        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
-        is a reconcilable difference with our simulated results.  
+	of spots are located on the simulated patterns
+	\item We confirmed this conclusion by radially integrating the 2D WAXS pattern for q values
+	between 1.57 and 1.4 (real space between 4 and 4.5 \AA) 
+	\item We observe that distinct peaks appear c.a. 30 $\degree$, in close agreement with the
+	previously measured angle distribution (~\ref{fig:offset_integration}~\ref{fig:layered_integration})
+%	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
+	\item We performed the same integration on the raw experimental data and found the angle
+	at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a 
+	reconcilable difference with our simulated results.  
   \end{itemize}
@@
 	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
-		        \caption{}~\label{fig:layered_tails}
+		        \caption{}~\label{fig:offset_integration}
 		\end{subfigure}
@@
 		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
-		        \caption{}~\label{fig:test}
+		        \caption{}~\label{fig:layered_integration}
 		\end{subfigure}
@@
   neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
-  same peaks are visible when the 2D simulated diffraction data is radially integrate in the R-alkanes region,
+  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
   (b) and (d) respectively.}~\label{fig:tail_packing}
@@
 	\item However, once the system has formed the Col\textsubscript{h} 
-	phase, adding water only creates disorder in the structure
+	phase, adding water only drives disorder in the structure
 	\item In the equilibrium configuration, if water exists, it is confined
@@
 	water molecules. 
-	\item The packing of water molecules will be too sparse to form a 
-	hydrogen bonding network.
+	\item In the case of trace water, water molecules will be too sparse to
+	form a hydrogen bonding network.
   \end{itemize}
@@
 	\item Much longer simulations are needed to lower the uncertainty, however it
-	is unfeasible to do so with large model. 
+	is not feasible to do so with a large model. 
 	\item For this reason we will likely only use the Nernst Einstein relation
@@
   \begin{itemize}  %BJC: working on the following. The following is what I expect
-  	\item There is an even distribution of crosslinks between same monomer tails, 
-	between monomers in the same pore and between monomers in different pores 
-	including periodic boundaries.  % BJC: might leave this detail in the supplemental
+%  	\item There is an even distribution of crosslinks between same monomer tails, 
+%	between monomers in the same pore and between monomers in different pores 
+%	including periodic boundaries.  % BJC: might leave this detail in the supplemental
 	\item We reach 95 \% conversion of terminal vinyl groups % BJC: we'll see
-	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
-	crosslinked  % probably smaller
-	\item We simulated the crosslinked simulations in the NPT ensemble for 100 ns
-	\item Major features are still present in the X-ray diffraction ~\ref{fig:rzplot_xlink} % BJC: maybe
-	\item The ionic conductivity is higher/lower in the crosslinked system ~\ref{fig:ic_xlink} % BJC: Nernst-Einstein is lower. Need a longer simulation to check Collective-Diffusion 
+	\item The distance between pores shrinks by 0.4\angstrom~ after the system is 
+	crosslinked  
+	\item We simulated the crosslinked system in the NPT ensemble for 100 ns
+	\item Major features are still present in the X-ray diffraction, however at lower intensities ~\ref{fig:rzplot_xlink} 
+	\item The ionic conductivity is lower in the crosslinked system ~\ref{fig:ic_xlink} % BJC: Nernst-Einstein is lower.
+Need a longer simulation to check Collective-Diffusion - I can probably avoid that by saying that we will be sticking with the Nernst-Einstein method
   \end{itemize}
@@
 	\centering
-	\includegraphics[widht=\textwidth]{rzplot_xlink.png}
+	\includegraphics[width=\textwidth]{rzplot_xlink.png}
 	\caption{}~\label{fig:rzplot_xlink}

### 2017-11-28 Ben_Manuscripts/structure_paper/Outline.tex
Added comments on outline.

@@
     \item Separation based on differences in solubility and diffusivity:
+%MRS2: couldn't you argue that the fact that they diffuse and dissolve at different rates means that it makes it possible to  design targeted separations?
     Moreover, designing RO membranes to achieve targeted separations of 
@@
     one nanometer in size.
+%MRS2: is ``well-defined'' the right word if there is a ``pore size distribution''?
     \item Larger and well-defined pores drive down energy requirements while
@@
     selectivity by tuning shape, size and functionality of the molecular
-    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant?
+    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant? %MRS2: seems fine for now, we can tweak this later. 
     \item As a result, solute rejecting pores can have their sizes tuned
@@
     % BJC: New paragraph?
+    %MRS2: shorter paragraphs generally good.
     \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
     aligned, resulting in low flux membranes, slowing research in the field.
+%MRS2: slowed research because it wasn't clear there was a route to scaleable filtration.
     \item In 2014, Feng et al. showed that the mesophases could be aligned 
@@
     reinvigorated.
-  \end{itemize}
-
-  % BJC: Not sure this figure needs to be in the paper
+%MRS2: not THAT many people are doing it, so hard to say reinvigorated quite yet. Pick other verb.
+  \end{itemize}
+
+  % BJC: Not sure this figure needs to be in the paper. 
+  %MRS2: good question.  It helps give people context, which is necessary to move forward.  Perhaps 
+  %leave it in for now, though may need to get permission to reprint it.
   \begin{figure}
@@
     to Na-GA3C11 with some characterization done after minor structural modifications
+%MRs: specify what type of modification.
     \cite{resel_structural_2000}.
@@
     solutes less than 1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
-    \item  We do not yet understand how to reduce the effective pore size or 
+    \item  We do not yet understand how to reduce the effective pore size 
+%MRS2: controllably
+      or 
     how to tune the chemical environment in the nanopores for effective water
@@
     which likely do not adequately describe transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
+%MRS2: not quite sure of the phrasing here on next two points. Something more a long the lines of the choice of head group 
+may allow tuning rejection of solutes based on size?
     \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
@@
   %BJC: Figure here showing previous level of detail compared to atomistic level of detail
+  %MRS2: provenance of the atomistic figure could be explained better in the caption. It also looks disordered. Will eventually need a higher resolution figure for the previous understanding pore.
   \begin{figure}
@@
 	    more detailed experimental structural data.  % BJC: More detailed because of WAXS. HII doesn't have any (that I know of) WAXS
+%MRS2: explicitly state the presence of WAXS data.
 	    \item Despite having structural data, there is still information which 
 	    experiment cannot definitively answer.
+            %MRS2: such as?
     \end{itemize}
@@
   answer in literature regarding the number of monomers in each layer. We want to
-  know (1) If layers do exist, how many monomers constitute a single layer?
+  know 
+\begin{enumerate}
+\item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}
   \begin{itemize}
@@
 
-  (2) Does our model support the existence of layers and if so, how well defined
-  are the layers?
+ \item Does our model support the existence of layers and if so, how well defined
+  are the layers? \label{point:layers}
   \begin{itemize}
@@
 
-   (3) How do monomers in each layer position themselves with respect to surrounding 
-   layers?
+   \item How do monomers in each layer position themselves with respect to surrounding 
+   layers? \label{point:orientation}
 %     Even if we knew the number of monomers in each layer, we still would not know how 
@@
 
-   (4) Is it necessary to include any water in order to appropriately model the 
-   Col\textsubscript{h} phase?
+   \item Is it necessary to include any water in order to appropriately model the 
+   Col\textsubscript{h} phase? \label{point:water}
    \begin{itemize}
@@
    \end{itemize}
-
+    \end{enumerate}
+%MRS2: size and how well well defined the pore is (how suddenly the RDF changes in the pore) is also a question.
+
+%MRS2: hmm.  This last point still seems somewhat relevant.  Why left out?
 %     \item While we might be able to provide answers to these questions using a 
@@
   \end{itemize}
-
+%MRS2: and potentially used to help design membranes.  
   \section*{Methods}
@@
   provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
-  assigned using tools from Openeye Scientific Software. All molecular dynamics 
-  simulations were run using the latest version of Gromacs 2016. 
+  assigned using tools from Openeye Scientific Software. 
+%MRS2: be specific what tools
+All molecular dynamics 
+  simulations were run using the latest version of Gromacs 2016. %MRS2: give specific version, since latest may be different when this is published.
   \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
@@
     and charges were reassigned using the am1bccsym method of molcharge
-    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
+    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite? %MRS2: webpage if no publication, 
     \item Using the new charges, the monomer system was annealed again and monomer
@@
 And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
+    %MRS2: I was referring to the data choice of 20 vs 10.  Yes, you can refer to it here, because the expectation is that peple will only look at it after reading the whole paper.
     \item We chose initial guesses for the remaining structural parameters based on
@@
         pattern shown in Figure~\ref{fig:WAXS}.
-        \item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
+        \item The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
         corresponding to a real spacing of 3.7 \angstrom~. The reflection is
@@
 
+%MRS2: make it clear these choices are for INITIAL spacing, and that this adjusted based on MD.  Also want to make
+sure the dependence of the initial choices is described in supporting information, as the results shouldn't be TOO dependnt on thesechoices.
   We chose the initial layer spacing based on R-$\pi$.
@@
     be parallel to the xy plane.
+%MRS2: seems like the choice of separation distance here should be detailed in the supporting information, and how it changes  the structures formed.  Also, not quite clear. 
     \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
@@
     %BJC: Do bootstrapping details go in supplemental?
+    %MRS2: yes.
     	% Supplemental vvvv
 	\begin{itemize}
+        %MRS2: make clear sampling what? 
     	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
@@
         a perfect hexagonal array. Only 4 are independent  
+        % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
         % Supplemental ^^^^
@@
 %  rejection data
+%MRS2: maybe this fits somewhere else, since it's not really used in the same way - it's more descriptive.
+In fact, maybe better to say it WASN'T used at all to constrain initial choice, and we simply looked at it after to understand how the pore size is affected by other choices.
+Or maybe I'm still misunderstanding.
+
   We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
@@
 
+%MRS2: is the pore radius of the initial configuration really relevant? Does it need to be defined?  Seems like what radius means in the final equilibrated one is more important.
   \begin{figure}
@@
 
+%MRS2: seems like the number per layer might be listed here, since that was adjusted during the fitting process?
+Hmm.
+I see it's later in the results.
+It's a bit confusing what variables are listed here (initial geometry settings), and what is discussed in the results section.
+(like number per layer)  We should discuss.
+
   %We tested a number of equilibration schemes of increasing complexity in an effort
@@
       \begin{itemize}
+        %MRS2: what initial force constant, and does it matter (that can be in supplemental) 
           \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
@@
           \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
-          slowly released until there is no more restraining potential.
+          slowly released 
+          %MRS2: be more quantitative about what ``slowly'' means.
+          until there is no more restraining potential.
           \item The resulting unrestrained structure is allowed to equilibrate for 5 ns 
@@
       \end{itemize}
-      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1 % BJC: supplemental?
+      \item In all cases, %MRS2: for system equilibration?
+the v-rescale thermostat was used with tau-t = 0.1 % BJC: supplemental? %MRS2: probably here.
   \end{itemize}
@@
     \item We matched experimental 2D WAXS patterns by iterative improvement
+%MRS2: The phrase ``iterative improvement'' isn't enough for someone to repeat the procedure.  Adjusted initial distances between layers?  
      of our choice of initial structure and equilibration procedure.
@@
 
-%  To discern the composition of the monomer layers, addressing (2), we ran 
-%  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
+%  To discern the composition of the monomer layers, addressing \ref{point:layers}, we ran 
+%  simulations of systems created with 4 - 8 monomers per layer.
+% BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
+%MRS2: ``with between'', I'd say.
   %\begin{itemize}
@@
 
-  To discern the composition of the monomer layers, addressing (1), we ran
+%MRS2: suggest starting with conclusion.
+Something like ``The simulations best support the model of 5 monomers per layer based on the pore-to-pore distances.'' Then provide evidence.
+Suggest for all points.
+
+  To discern the composition of the monomer layers, addressing (\ref{point:monomernum}), we ran
   simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
@@
   %BJC: maybe split into 2 paragraphs
-  To answer (2), we verified that the system stays partitioned into layers by
+  %MRS2: usually good instinct.
+Lead with the conclusions of the research you are trying to convince readers.
+Rather than phrasing as a question.
+Something like: ``Layers are well defined and persistent''.
+  To answer (\ref{point:layers}), we verified that the system stays partitioned into layers by
   plotting the pair correlation function, $g(z)$ calculated between atoms along
@@
 	and, separately, with respect to carbon atoms on the alkane chains.
-	\item In both cases, we see a degree of layer partitioning
+	\item In both cases, we see 
+%MRS2: more precise than ``a degree''?
+a degree of layer partitioning
         \item Using the head groups as reference, we see that sandwiched configuration
@@
         Supplemental Information.  %BJC: "Power spectrum" an okay description here?
+        %MRS2: repore more precisely what finding is interesting. What does that difference mean?
 	\item We see a difference in the spacing in the head group versus tail region
@@
         number density by 61 \%. %BJC: I mention how I do this calculation in the methods. Is it clear that I'm doing that here?
+%MRS2: fine for description for now.          
 	\item The parallel displaced configuration deviates from the mean by only 
 	12 \% in comparison.
+%MRS2: is this that unexpected, since parallel displaces should have layers that alternate anyway?
   \end{itemize}
@@
   % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information 
-
+  %MRS2: good.
   \begin{figure}
@@
 
-  We answer question (3) by simulating X-ray diffraction patterns produced from
+  We answer question (\ref{point:orientation}) by simulating X-ray diffraction patterns produced from
   equilibrated MD trajectories.
@@
         shows R-spots}\label{fig:tails}
+        %MRS2: might need to say how the dynamic range is adjusted here with only tails, since otherwise people will be confused with the R-spots being more intense. 
   \end{figure}
@@
   (b) and (d) respectively.}~\label{fig:tail_packing}
+%MRS2: not clear what the difference is between right and left side figures.
   \end{figure}
 
-  We answer (4) and further support (3) by preparing parallel displaced and
+  We answer (\ref{point:water}) and further support (\ref{point:orientation}) by preparing parallel displaced and
   sandwiched configurations according to the wet equilibration procedure.
@@
 	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
+        %MRS2: include 0% as well? Maybe leave off 5% if not relevant in the end?
 	\label{fig:solvation}
@@
 	\item Much longer simulations are needed to lower the uncertainty, however it
-	is not feasible to do so with a large model. 
+	is not feasible to do so with a large model. %MRS2: large system. 
 	\item For this reason we will likely only use the Nernst Einstein relation
@@
   % BJC: I'll also see what I can do about all the white speckles
+%MRS2: I'm not sure what the point of this figure is?
   \caption{The experimental two dimensional SAXS pattern exhibits reflections
@@
   would exhibit sharp dots at the same locations of the refelctions shown. 
-  An isotropically aligned system the refelctions would appear as 
+  An isotropically aligned system the reflections would appear as 
   rings centered about the origin}~\label{fig:2DSAXS}
@@
 	\item We were able to deduce that layers are composed of 5 monomers 
+          %MRS2: be more precise about conclusions: evidence strongly supports 5 monomers / layer.
         \item We have confirmed that monomers stay partitioned in layers.
@@
 	\item Finally, water is not needed to maintain membrane structure 
+          %MRS2: Maybe ``water disorders the pore'' (some thought it might order it).
 	\item Now that we have a good idea of what the membrane structure should look like, we will
 	evaluate transport of various solutes within the system. 
+         %MRS2: I'd like to see a bit more information about ``pore size'', and the RDF's of the constituents.  What FITS through a pore is another paper.
         \item We will apply the knowledge gained from this study in order to 

### 2017-11-28 Ben_Manuscripts/structure_paper/Outline.tex
Addressed what comments I could and did some minor reorganization

@@
 %MRS2: couldn't you argue that the fact that they diffuse and dissolve at different rates means that it makes it possible to design targeted separations?
+%BJC: right, I say something like that in the sentence following this one. It would be more challenging to design a targeted separation 
+% especially if the feed is complex
     Moreover, designing RO membranes to achieve targeted separations of 
-    specific solutes is nearly impossible because various solutes dissolve
+    specific solutes in a complex feed solution is nearly impossible because various solutes dissolve
     into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
-    \item At best, one can exploit these differences to create a functional
+    \item With optimization, one can exploit these differences to create a functional
     selective barrier.
@@
 %MRS2: is ``well-defined'' the right word if there is a ``pore size distribution''?
+%BJC: By well-defined, I'm thinking of cylinders versus polymer matrix. One is definitely more
+% defined than the other. What is the right word for that? unambiguous? explicit?
     \item Larger and well-defined pores drive down energy requirements while
@@
     selectivity by tuning shape, size and functionality of the molecular
-    building blocks which form these materials. % BJC: "these materials" --> "nanostructured membranes", or is that redundant? %MRS2: seems fine for now, we can tweak this later. 
+    building blocks which form these materials. 
     \item As a result, solute rejecting pores can have their sizes tuned
@@
     zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
-    % BJC: New paragraph?
-    %MRS2: shorter paragraphs generally good.
-    \item Until recently, mesophases formed by Na-GA3C11 could not be macroscopically
-    aligned, resulting in low flux membranes, slowing research in the field.
-%MRS2: slowed research because it wasn't clear there was a route to scaleable filtration.
+  \end{itemize}
+
+  Research into LLC membranes has been revived in recent years.
+  \begin{itemize}
+    \item During early stages of exploration, mesophases formed by Na-GA3C11 could not be macroscopically
+    aligned, resulting in low flux membranes, and no clear route towards 
+    scalable and economical filtration. 
     \item In 2014, Feng et al. showed that the mesophases could be aligned 
@@
     using a technique termed soft confinement \cite{feng_thin_2016}.
-    \item Following this breakthrough, research into LLC membranes has been
-    reinvigorated.
-%MRS2: not THAT many people are doing it, so hard to say reinvigorated quite yet. Pick other verb.
   \end{itemize}
@@
   \begin{itemize}
-%     \item LLCs are versatile and controllable with a \textbf{large chemical design
-%     space} available for membrane design  %BJC: redundant
     \item Over the past 20 years, H\textsubscript{II} phase LLC membrane studies have been limited primarily
     to Na-GA3C11 with some characterization done after minor structural modifications
-%MRs: specify what type of modification.
-    \cite{resel_structural_2000}.
+    \item Resel et al. varied the length of the monomer tails and the counterion used and 
+    observed its affect on pore spacing \cite{resel_structural_2000}.
     \item Rejection studies show that this membrane can not perform separations of
     solutes less than 1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
-    \item  We do not yet understand how to reduce the effective pore size 
-%MRS2: controllably
-      or 
+    \item  We do not yet understand how to controllably reduce the effective pore size or 
     how to tune the chemical environment in the nanopores for effective water
@@
 %MRS2: not quite sure of the phrasing here on next two points. Something more a long the lines of the choice of head group 
-may allow tuning rejection of solutes based on size?
-    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
+%may allow tuning rejection of solutes based on size?
+%BJC: okay tried again
+    \item The choice of head group may allow us to tune pore size for size exclusion driven separations
     \item Choice of counterion may influence the establishment of a Donnan potential
@@
   %MRS2: provenance of the atomistic figure could be explained better in the caption. It also looks disordered. Will eventually need a higher resolution figure for the previous understanding pore.
+  %BJC: Okay. The picture here is of the "ordered pore" phase. It looks disorderd from this angle. I could use a different slice of the membrane to see if it looks any better
   \begin{figure}
@@
 	   about separation behavior. (b) A detailed molecular model will allow us to
-	   directly observe solute transport}~\label{fig:detail}
+	   directly observe solute transport. Here, four stacked layers of 5 monomers
+           are pictured atomistically. The hydrophilic region is in red and the 
+	   hydrophoic region is colored blue.}~\label{fig:detail}
   \end{figure}
@@
 	    phase is a simpler starting point, due to the absence of water, and has
-	    more detailed experimental structural data.  % BJC: More detailed because of WAXS. HII doesn't have any (that I know of) WAXS
-%MRS2: explicitly state the presence of WAXS data.
-	    \item Despite having structural data, there is still information which 
-	    experiment cannot definitively answer.
-            %MRS2: such as?
-    \end{itemize}
+	    detailed experimental WAXS patterns useful for reconstructing structural data.  
+    \end{itemize}
+
+  Despite having structural data, there is still information which
+  experiment cannot definitively answer. There are several key
+  questions that we intend to answer which will be laid out and numbered
+  in subsequent paragraphs.
 
@@
 And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)
-
-  Despite having structural data, there is still information which 
-  experiment cannot definitively answer. There are several key 
-  questions that we intend to answer which will be laid out and numbered
-  in subsequent paragraphs.
 
@@
     \end{enumerate}
-%MRS2: size and how well well defined the pore is (how suddenly the RDF changes in the pore) is also a question.
+%MRS2: size and how well defined the pore is (how suddenly the RDF changes in the pore) is also a question.
 
 %MRS2: hmm.  This last point still seems somewhat relevant.  Why left out?
+%BJC: I thought we agreed to leave this out. It lengthens the paper and makes it
+% more confusing. Unless we just want to hint at it.
+
 %     \item While we might be able to provide answers to these questions using a 
@@
     \item The structure-building approach and analysis used in this paper can be readily extended
-    to the H\textsubscript{II} phase and other similar LC systems.
-  \end{itemize}
-%MRS2: and potentially used to help design membranes.  
+    to the H\textsubscript{II} phase, other similar LC systems and ultimately to help design
+    real membranes.
+  \end{itemize}
+
   \section*{Methods}
@@
   provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
-  assigned using tools from Openeye Scientific Software. 
-%MRS2: be specific what tools
-All molecular dynamics 
-  simulations were run using the latest version of Gromacs 2016. %MRS2: give specific version, since latest may be different when this is published.
+  assigned using the am1bccsym method of molcharge shipped with QUACPAC from Openeye % cite with webpage
+  Scientific Software. All molecular dynamics simulations were run using Gromacs 2016  % This the version on Bridges
   \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
@@
     \item A low energy configuration was randomly pulled from the trajectory
-    and charges were reassigned using the am1bccsym method of molcharge
-    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite? %MRS2: webpage if no publication, 
+    and charges were reassigned with molcharge. 
     \item Using the new charges, the monomer system was annealed again and monomer
@@
     infinite length pore ideal for studying transport.
+    \item Each layer is made of a set number of monomers per layer, a variable to
+    be explored further.
     \item A small number of layers is preferred in order to reduce computational
@@
 %MRS2: make it clear these choices are for INITIAL spacing, and that this adjusted based on MD.  Also want to make
-sure the dependence of the initial choices is described in supporting information, as the results shouldn't be TOO dependnt on thesechoices.
-  We chose the initial layer spacing based on R-$\pi$.
+%sure the dependence of the initial choices is described in supporting information, as the results shouldn't be TOO dependnt on thesechoices.
+%BJC: okay will work on some figures illustrating the affect of initial choices on results
+  We chose the layer spacing for the initial configuration based on R-$\pi$ and then allowed system
+  to readjust during equilibration.
   \begin{itemize}  
@@
 %MRS2: seems like the choice of separation distance here should be detailed in the supporting information, and how it changes  the structures formed.  Also, not quite clear. 
+%BJC: okay, I have some ideas for this
     \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
@@
     \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
-    %BJC: Do bootstrapping details go in supplemental?
-    %MRS2: yes.
     	% Supplemental vvvv
@@
         %MRS2: make clear sampling what?
+        \item We are interested in 5 pore-to-pore distances which should all be equal in
+        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
+	\item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
+	the system is equilibrated, we calculate how long it takes for the data in each of the 5
+	trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
+	\item We break the full trajectories down into sub-trajectories based on the
+	maximum autocorrelation time of those found in the previous step. 
     	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
-    	sampling from the original trajectory
-    	\item Each pore spacing has its own trajectory with its own average value
-    	\item The average value of each pore spacing is averaged to get the overall
-    	average pore spacing. 
-    	\item The standard deviation of average values is reported as the uncertainty in pore spacing
-    	% BJC: The following will go in supplemental
-        \item We are interested in 5 pore-to-pore distances which should all be equal in 
-        a perfect hexagonal array. Only 4 are independent  
+    	sampling pore spacings from the sub-trajectories 
+    	\item We get an average value for each pore spacing by finding the mean of the bootstrapped data
+	\item We calculate the overall average as the mean of all bootstrapped pore spacings
+	\item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
+	average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
+	\item We report the mean of these uncertainties
         % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
+	% BJC: Updated
         % Supplemental ^^^^
@@
 %MRS2: is the pore radius of the initial configuration really relevant? Does it need to be defined?  Seems like what radius means in the final equilibrated one is more important.
+%BJC: maybe not, we'll have to talk to get on the same page
   \begin{figure}
@@
         %MRS2: what initial force constant, and does it matter (that can be in supplemental) 
+	%BJC: I've never explored whether there is any dependence on initial force constant. It probably doesn't matter unless it starts really low
           \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
@@
           \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
-          slowly released 
-          %MRS2: be more quantitative about what ``slowly'' means.
-          until there is no more restraining potential.
+          released linearly until there is no more restraining potential.
           \item The resulting unrestrained structure is allowed to equilibrate for 5 ns 
@@
       \end{itemize}
-      \item In all cases, %MRS2: for system equilibration?
-the v-rescale thermostat was used with tau-t = 0.1 % BJC: supplemental? %MRS2: probably here.
+      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1 % BJC: supplemental
   \end{itemize}
@@
     experimentally.
-    \item We matched experimental 2D WAXS patterns by iterative improvement
-%MRS2: The phrase ``iterative improvement'' isn't enough for someone to repeat the procedure.  Adjusted initial distances between layers?  
-     of our choice of initial structure and equilibration procedure.
+    \item We matched experimental 2D WAXS patterns by adjusting the initial 
+    spacing between layers and the orientation of the head groups with respect
+    to adjacent layers.
   \end{itemize}
@@
     \item Sodium ion diffusion coefficients were found by calculating the slope
-    of the linear region of the mean square displacement curve as indicated by
+    of the linear region of the z-direction mean square displacement curve as indicated by
     the einstein relation \cite{einstein_investigations_1956}.]
@@
 
-  To discern the composition of the monomer layers, addressing (\ref{point:monomernum}), we ran
-  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
+  The simulations best support a model built with 5 monomers per layer based on 
+  the measured pore-to-pore distances. To discern the composition of the monomer 
+  layers, addressing (\ref{point:monomernum}), we ran simulations of systems created
+  with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
   \begin{itemize}
@@
         \item All systems are stable after 400 ns of simulation.  
-        \item Table ~\ref{fig:p2p} shows the pore spacing for all systems tested.
+        \item Figure ~\ref{fig:p2p} shows the pore spacing for all systems tested.
         \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
@@
 Something like: ``Layers are well defined and persistent''.
-  To answer (\ref{point:layers}), we verified that the system stays partitioned into layers by
+  We learned that layers are well-defined and persistent, answering (\ref{point:layers})
+  %We verified that the system stays partitioned into layers by
+  We verified our conclusion by
   plotting the pair correlation function, $g(z)$ calculated between atoms along
@@
 	and, separately, with respect to carbon atoms on the alkane chains.
-	\item In both cases, we see 
-%MRS2: more precise than ``a degree''?
-a degree of layer partitioning
+	% \item In both cases, we see a degree of layer partitioning
         \item Using the head groups as reference, we see that sandwiched configuration
@@
 %MRS2: is this that unexpected, since parallel displaces should have layers that alternate anyway?
+%BJC: true, but I'm just stating the facts
   \end{itemize}
@@
 
+  %BJC: Put this paragraph first since it is the conclusion I want to stick
+  The parallel displaced configuration results in a simulated XRD pattern with
+  the closest match to experiment.
+  \begin{itemize}
+        \item It produces the only pattern that exhibits all major reflections
+        \item R-alkanes, R-pores and R-$\pi$ appear as they do in the sandwiched configuration.
+        \item R-spots appears, however with a lower intensity relative to R-alkanes
+        when compared to the sandwiched configuration.
+        \item R-helix appears apparently due to the parallel displaced aromatic rings
+        %BJC: Maybe a figure to explain why this happens
+  \end{itemize}
+
+  %BJC: Put this paragraph second so people understand why it is wrong and don't fixate on how nice the spots are
   Simulated XRD of the sandwiched configuration contains all experimental features
@@
         to such features. 
-  \end{itemize}
-
-  The parallel displaced configuration results in a simulated XRD pattern with 
-  the closest match to experiment. 
-  \begin{itemize}
-	\item It produces the only pattern that exhibits all major reflections
-	\item R-alkanes, R-pores and R-$\pi$ appear as they do in the sandwiched configuration. 
-	\item R-spots appears, however with a lower intensity relative to R-alkanes
-        when compared to the sandwiched configuration.
-        \item R-helix appears apparently due to the parallel displaced aromatic rings
-        %BJC: Maybe a figure to explain why this happens
   \end{itemize}
@@
         %MRS2: might need to say how the dynamic range is adjusted here with only tails, since otherwise people will be confused with the R-spots being more intense. 
+	%BJC: what do you mean by dynamic range?
   \end{figure}
@@
 %MRS2: not clear what the difference is between right and left side figures.
+%BJC: That's good! One is angles measured between tail centroids and the other is radial integration of the simulated xrd patterns. I'll try make that more clear in the caption.
   \end{figure}
@@
 	\item Much longer simulations are needed to lower the uncertainty, however it
-	is not feasible to do so with a large model. %MRS2: large system. 
+	is not feasible to do so with a large system.  
 	\item For this reason we will likely only use the Nernst Einstein relation
@@
 %MRS2: I'm not sure what the point of this figure is?
+%BJC: I put it here at some point in case the need arises. It's mainly to show
+% that the pores in the real system are somewhat tortuous, in place of showing
+% the Azimuthal distribution which is just an integration of this data. I thought
+% it'd be clearer that way since but maybe it's not?
   \caption{The experimental two dimensional SAXS pattern exhibits reflections
@@
 	attempt to examine their structure with the same level of detail presented here.
-	\item We were able to deduce that layers are composed of 5 monomers 
-          %MRS2: be more precise about conclusions: evidence strongly supports 5 monomers / layer.
+	\item Evidence strongly supports that layers are composed of 5 monomers
         \item We have confirmed that monomers stay partitioned in layers.
@@
 	the parallel-displaced configuration produces a structure with the closest match to experiment.
-	\item Finally, water is not needed to maintain membrane structure 
-          %MRS2: Maybe ``water disorders the pore'' (some thought it might order it).
+	\item Finally, water is not needed to maintain membrane structure our data 
+	shows that it actually disorders the pore
 	\item Now that we have a good idea of what the membrane structure should look like, we will

### 2017-11-28 HII/Scripts/Ionic_Conductivity.py

@@ -1,5 +1,24 @@
 #! /usr/bin/env python
 
+from __future__ import division
+from __future__ import print_function
+from __future__ import absolute_import
+
+from builtins import range
+from past.utils import old_div
+import argparse
+import Atom_props
+import matplotlib.pyplot as plt
+import time
+import Poly_fit
+import numpy as np
+import Diffusivity
+import Concentration
+import subprocess
+import mdtraj as md
+from llclib import physical
+import tqdm
+
 """
 The purpose of this script is to calculate the ionic conductivity of a given LLC membrane using the Nernst Einstein
 relation (Method 1) and the Collective Diffusion model (Method 2), the latter being described in the following paper:
@@ -67,52 +86,39 @@ across the membrane (which can be found using gmx potential with a careful look 
 One can also employ the Computational Electrophysiology Module included with GROMACS to create a double layer membrane
 system which maintains a concentration gradient across the membrane, inducing a current.
 """
-from __future__ import division
-from __future__ import print_function
-from __future__ import absolute_import
-
-from builtins import range
-from past.utils import old_div
-import argparse
-import Atom_props
-import matplotlib.pyplot as plt
-import time
-import Poly_fit
-import numpy as np
-import Diffusivity
-import Concentration
-import subprocess
-import mdtraj as md
-from llclib import physical
 
 
 def initialize():
 
-    parser = argparse.ArgumentParser(description = 'Calculate Ionic Conductivity using the Nernst Einstein relation or'
-                                                   'the Collective Diffusion Model')
+    parser = argparse.ArgumentParser(description='Calculate Ionic Conductivity using the Nernst Einstein relation or'
+                                                 'the Collective Diffusion Model')
 
     parser.add_argument('-t', '--traj', default='wiggle.trr', type=str, help='Trajectory file (.xtc or .trr)'
-                                                   'IMPORTANT: Pre-process the trajectory with gmx trjconv -pbc nojump')
+                                                                             'IMPORTANT: Pre-process the trajectory with gmx trjconv -pbc nojump')
     parser.add_argument('-g', '--gro', default='wiggle.gro', type=str, help='Coordinate file')
[…]

### 2017-11-28 HII/Scripts/zdf.py

@@ -27,6 +27,7 @@ def initialize():
     parser.add_argument('-apl', default=5, type=float, help='Atoms or monomers per layer')
     parser.add_argument('-l', '--load', type=str, help='Load compressed numpy array')
     parser.add_argument('-com', '--com', action="store_true", help='Calculate zdf based on com of atoms')
+    parser.add_argument('-r', '--res', type=str, help='Residue name to calculate zdf of')
 
     args = parser.parse_args()
 
@@ -66,6 +67,7 @@ def z_periodic(positions, unitcell_vectors, images=1):
     :return: new positions with n images in the +/- z direction where n=images
     """
 
+    # use cKDTree to make this way faster
     nT = positions.shape[0]
     natoms = positions.shape[1]
     nimages = images*2 + 1
@@ -270,6 +272,7 @@ if __name__ == "__main__":
 
     t = md.load(args.traj, top=args.gro)[args.begin:args.end:args.skip]
     frame = t.slice(0)
+
     # from llclib import file_rw
     # file_rw.write_gro(frame, 'first.gro')
     # exit()
@@ -283,7 +286,6 @@ if __name__ == "__main__":
         z = zdf["z"]
         bin_width = (z[1] - z[0])
         ps, freqs, max = power_spectrum(zdf_avg, bin_width)
-        print(freqs.shape)
         # dbwl, amp = spacing(z, zdf_avg)
         print('Fourier distance between layers: %s nm' % (1/max))
         # print('Amplitude of first peak : %2.2f %% of mean' % (100*(amp/np.mean(zdf_avg[:z.shape[0]]))))
@@ -321,9 +323,13 @@ if __name__ == "__main__":
 
         for atom in args.atoms:
 
-            keep = [a.index for a in t.topology.atoms if a.name == atom]
+            if args.res:
+                keep = [a.index for a in t.topology.atoms if a.name == atom and a.residue.name == args.res]
+            else:
+                keep = [a.index for a in t.topology.atoms if a.name == atom]
 
-            pos = t.atom_slice(keep).xyz
+            # pos = t.atom_slice(keep).xyz
+            pos = t.xyz[:, keep, :]
 
             periodic = z_periodic(pos, box)
 

### 2017-12-01 Ben_Manuscripts/structure_paper/Outline.tex
comments on outline
Updated with better organization and some new figures

@@
 
+  \item Can the system exist in other metastable states or phases that are not
+  accessed during experiments? \label{point:metastable}
+  There remains the possibility that there is more than one metastable state 
+  associated with a given LLC system.
+  \begin{itemize}
+    \item Simulating a membrane atomistically will require many atoms which further
+    limits the timescales acessible with MD
+    \item It is reasonable to expect that we will generate configurations which 
+    are kinetically trapped in a metastable free energy basin
+    \item We must be able to identify which state is produced experimentally and 
+    why others are not.
+  \end{itemize}
+
+  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
+  \begin{itemize}
+	\item The limited picture that experiment provides tells us that there are
+        hexagonally packed, hydrophilic regions where transport is likely to occur
+	\item One may instinctively assume that these regions are tube-like pathways
+	\item We will explore the composition of the pores and the partition
+	between the hydrophilic and hydrophobic regions. 
+  \end{itemize}
+
   \item Is it necessary to include any water in order to appropriately model the 
@@
   \end{enumerate}
-%MRS2: size and how well defined the pore is (how suddenly the RDF changes in the pore) is also a question.
-
-%MRS2: hmm.  This last point still seems somewhat relevant.  Why left out?
-%BJC: I thought we agreed to leave this out. It lengthens the paper and makes it
-% more confusing. Unless we just want to hint at it.
-
-%     \item While we might be able to provide answers to these questions using a 
-%     molecular model, there remains the possibility that there is more than one 
-%     metastable state associated with a given LLC system.
-
-%  (4) Can the system exist in other metastable states or phases that are not
-%  accessed during experiments?
-%  There remains the possibility that there is more than one metastable state 
-%  associated with a given LLC system.
-%  \begin{itemize}
-%    \item Simulating a membrane atomistically will require many atoms which further
-%    limits the timescales acessible with MD
-%    \item It is reasonable to expect that we will generate configurations which 
-%    are kinetically trapped in a metastable free energy basin
-%    \item We must be able to identify which state is produced experimentally and 
-%    why others are not.
-%  \end{itemize}
 
@@
   %the system.
+
   In this study, we build a significantly more realistic atomistic model of LLC membranes
@@
     conductivity measurements~\cite{feng_thin_2016}.
-    \begin{itemize}
-	    \item We have compared simulated X-ray diffraction patterns to experiment in 
-	    order to match major features present in the 2D patterns.
-	    \item We calculated ionic conductivity using two agreeing methods.
-	    \item We examined the the influence of crosslinking on membrane structure.
-    \end{itemize}
-    \item The structure-building approach and analysis used in this paper can be readily extended
-    to the H\textsubscript{II} phase, other similar LC systems and ultimately to help design
-    real membranes.
-  \end{itemize}
-
-  \section*{Methods}
-
-  Liquid crystal monomers were parameterized using the Generalized AMBER Forcefield
-  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
-  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
-  assigned using the am1bccsym method of molcharge shipped with QUACPAC from Openeye % cite with webpage
-  Scientific Software. All molecular dynamics simulations were run using Gromacs 2016  % This the version on Bridges
-  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-
-  An ensemble of characteristic, low-energy vacuum monomer configurations
-  were constructed by applying a simulated annealing process to a
-  parameterized monomer.
-  \begin{itemize}
-    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
-    \item A low energy configuration was randomly pulled from the trajectory
-    and charges were reassigned with molcharge. 
-    \item Using the new charges, the monomer system was annealed again and monomer
-    configurations were pulled from the trajectory to be used for full
-    system construction (Figure~\ref{fig:python}a).
-  \end{itemize}
-
-  The timescale for self assembly of monomers into the hexagonal phase is
-  unknown and likely outside of a reasonable length for an atomistic
-  simulation, calling for a more efficient way to build the system. 
-  \begin{itemize}
-    \item Previous work has shown a coarse grain model self assemble into
-    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
-    \item We attempted atomistic self-assembly by packing monomers into a box 
-    using Packmol \cite{martinez_packmol:_2009}.
-    \item Simulations of greater than 100 ns show no indicators of progress 
-    towards an ordered system.  %BJC: include more details in supplment
-    \item To bypass the slow self-assembly process, python scripts are used
-    to assemble monomers into a structure close to one of a number of 
-    hypothesized equilibrium configurations (Figure~\ref{fig:python}).
-  \end{itemize}
-
-  \begin{figure}
-	\centering
-	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
-	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
-		configuration. (b) Monomers are rotated and assembled into layers with 
-		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
-		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
-  \end{figure}
-
-  A typical simulation volume contains four pores in a monoclinic unit cell,
-  the smallest unit cell that maintains hexagonal symmetry when extended 
-  periodically.
-  \begin{itemize}
-    \item Each pore is made of twenty stacked monomer layers with periodic 
-    continuity in the z direction, avoiding any edge effects and creating an 
-    infinite length pore ideal for studying transport.
-    \item Each layer is made of a set number of monomers per layer, a variable to
-    be explored further.
-    \item A small number of layers is preferred in order to reduce computational
-    cost and to allow us to look at longer timescales.
-    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
-    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
-    This point will be explained in more detail later.
-    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
-    %BJC: so refer to supporting info here?
-Then put plots of diffraction data with different sized system there.
-I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense.
-And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
-    %MRS2: I was referring to the data choice of 20 vs 10.  Yes, you can refer to it here, because the expectation is that peple will only look at it after reading the whole paper.
-    \item We chose initial guesses for the remaining structural parameters based on
-    experimental data and treated them as variables during model development.
   \end{itemize}
@@
 
+%    \begin{itemize}
+%            \item We have compared simulated X-ray diffraction patterns to experiment in
+%            order to match major features present in the 2D patterns.
+%            \item We calculated ionic conductivity using two agreeing methods.
+%            \item We examined the the influence of crosslinking on membrane structure.
+%    \end{itemize}
+%    \item The structure-building approach and analysis used in this paper can be readily extended
+%    to the H\textsubscript{II} phase, other similar LC systems and ultimately to help design
+%    real membranes.
+%  \end{itemize}
+
+  \section*{Methods}
+
+  %BJC: The Methods sections has four main topics which will be separated by an appropriate header
+
+  %%%%%%%%% Monomer Preparation %%%%%%%%%%%%%
+
+  Liquid crystal monomers were parameterized using the Generalized AMBER Forcefield
+  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
+  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
+  assigned using the am1bccsym method of molcharge shipped with QUACPAC from Openeye % cite with webpage
+  Scientific Software. All molecular dynamics simulations were run using Gromacs 2016  % This the version on Bridges
+  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
+
+  An ensemble of characteristic, low-energy vacuum monomer configurations
+  were constructed by applying a simulated annealing process to a
+  parameterized monomer.
+  \begin{itemize}
+    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
+    \item A low energy configuration was randomly pulled from the trajectory
+    and charges were reassigned with molcharge. 
+    \item Using the new charges, the monomer system was annealed again and monomer
+    configurations were pulled from the trajectory to be used for full
+    system construction (Figure~\ref{fig:python}a).
+  \end{itemize}
+
+  %%%%%%%% UnitCell Preparation %%%%%%%%%%%%%
+
+  The timescale for self assembly of monomers into the hexagonal phase is
+  unknown and likely outside of a reasonable length for an atomistic
+  simulation, calling for a more efficient way to build the system. 
+  \begin{itemize}
+    \item Previous work has shown a coarse grain model self assemble into
+    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
+    \item We attempted atomistic self-assembly by packing monomers into a box 
+    using Packmol \cite{martinez_packmol:_2009}.
+    \item Simulations of greater than 100 ns show no indicators of progress 
+    towards an ordered system.  %BJC: include more details in supplment
+    \item To bypass the slow self-assembly process, python scripts are used
+    to assemble monomers into a structure close to one of a number of 
+    hypothesized equilibrium configurations (Figure~\ref{fig:python}).
+  \end{itemize}
+
+  \begin{figure}
+	\centering
+	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
+	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
+		configuration. (b) Monomers are rotated and assembled into layers with 
+		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
+		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
+  \end{figure}
+
+  A typical simulation volume contains four pores in a monoclinic unit cell,
+  the smallest unit cell that maintains hexagonal symmetry when extended 
+  periodically.
+  \begin{itemize}
+    \item Each pore is made of twenty stacked monomer layers with periodic 
+    continuity in the z direction, avoiding any edge effects and creating an 
+    infinite length pore ideal for studying transport.
+%    \item Each layer is made of a set number of monomers per layer, a variable to
+%    be explored further.
+    \item A small number of layers is preferred in order to reduce computational
+    cost and to allow us to look at longer timescales.
+    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
+    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
+    This point will be explained in more detail later.
+    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
+    %BJC: so refer to supporting info here?
+Then put plots of diffraction data with different sized system there.
+I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense.
+And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
+    %MRS2: I was referring to the data choice of 20 vs 10.  Yes, you can refer to it here, because the expectation is that peple will only look at it after reading the whole paper.
+%    \item We chose initial guesses for the remaining structural parameters based on
+%    experimental data and treated them as variables during model development.
+  \end{itemize}
+
 %  We chose an initial layer spacing based on experimental 2D WAXS data.
@@
 
-%MRS2: make it clear these choices are for INITIAL spacing, and that this adjusted based on MD.  Also want to make
-%sure the dependence of the initial choices is described in supporting information, as the results shouldn't be TOO dependnt on thesechoices.
-%BJC: okay will work on some figures illustrating the affect of initial choices on results
-  We chose the layer spacing for the initial configuration based on R-$\pi$ and then allowed system
-  to readjust during equilibration.
+  %%%%%%%%%%%% Monomer Placement %%%%%%%%%%%%%%
+
+  When constructing an initial configuration, there are a number of variables
+  which require careful consideration while placing monomers. The equilibrium
+  configuration is sensitive to some while insensitive to others.
+  \begin{itemize}
+	\item The starting pore radius, defined as the distance of a chosen 
+        head group carbon from the pore's central axis, does not influence the
+        equilibrium structure when a reasonable value is chosen (See Supplemental)
+        \item The pore radius is chosen to be 0.6 nm in our initial configurations 
+        because the pore size is estimated to be $\approx$ 1.2 nm % Add reference
+	\item The initial distance between pores also has little effect on the 
+        the equilibrated structure. However, one should not start them too close or there 
+        will likely be unintended high energy repulsions during early equilibration
+	\item We chose an initial pore spacing of 4.5 nm, $\approx$ 10 \% larger than 
+        the experimental value of 4.12 nm.
+        \item The distance between layers and the rotation of the layers with respect
+        to adjacent layers, and the number of monomers per layer do influence the 
+        equilibrium structure and require further justification for their choices. 
+        \item We rely on experimental data to inform our choices
+  \end{itemize}
+
+  We chose the layer spacing for the initial configuration based on R-$\pi$ 
+  and then allowed system to readjust during equilibration.
   \begin{itemize}  
     \item Each monomer was rotated so the plane of the aromatic head groups would
-    be parallel to the xy plane.
-%MRS2: seems like the choice of separation distance here should be detailed in the supporting information, and how it changes  the structures formed.  Also, not quite clear. 
-%BJC: okay, I have some ideas for this
-    \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
-    apart in the z-direction.
-    \item To quantify the degree of layering in our system, we calculated
-    a spatial correlation function, $g(z)$, measured along the z-axis 
-    (perpendicular to the membrane plane)
-    \item To calculate $g(z)$, we binned the z component distances between 
-    the center of mass of each benzene ring and all others of the same pore 
-    over 50 ns of equilibrated trajectory and then normalized by the average
-    number density.
-    \item We compare the degree of layering between systems based on the
-    amplitude of the first peak in $g(z)$. We halve the difference between the
-    maximum of the first peak and the following minimum. We compare the difference
-    to the mean to get a percentage deviation from the average number density.
-    \item To extract the average distance between layers we applied a discrete 
-    fourier transform to $g(z)$ and extracted the highest intensity frequency 
-  \end{itemize}
-
-  We placed pores at a chosen initial spacing based on R-pores, then allowed
-  the system to settle into its preferred spacing. 
-  \begin{itemize}
+    be coplanar with the xy plane.
+    \item We explore two different initial layer spacings
+    \item The first is exactly equal to R-$\pi$ with layers placed so aromatic
+    rings are stacked 3.7 \angstrom~ apart in the z-direction.
+    \item A second system is explored with an initial layer spacing of 5 \angstrom
+    \item A third system with an initial layer spacing of 10 \angstrom was briefly
+    explored and the reader can learn more about it in the Supplemental Information.
+% BJC: Move all this lower down to be with the rest of the equilibrium calculations
+%    \item To quantify the degree of layering in our system, we calculated
+%    a spatial correlation function, $g(z)$, measured along the z-axis 
+%    (perpendicular to the membrane plane)
+%    \item To calculate $g(z)$, we binned the z component distances between 
+%    the center of mass of each benzene ring and all others of the same pore 
+%    over 50 ns of equilibrated trajectory and then normalized by the average
+%    number density.
+%    \item We compare the degree of layering between systems based on the
+%    amplitude of the first peak in $g(z)$. We halve the difference between the
+%    maximum of the first peak and the following minimum. We compare the difference
+%    to the mean to get a percentage deviation from the average number density.
+%    \item To extract the average distance between layers we applied a discrete 
+%    fourier transform to $g(z)$ and extracted the highest intensity frequency 
+  \end{itemize}
+
+% BJC: removing this since I say earlier that the system is insensitive to this choice
+% Detail will be provided in the supplement
+% discussion of measuring equilibrium pore spacing is moved down to calculations part of methods
+%  We placed pores at a chosen initial spacing based on R-pores, then allowed
+%  the system to settle into its preferred spacing. 
+%  \begin{itemize}
     %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
     %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
-    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
-    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
-    resulting from a tightly packed initial configuration.
-    \item To calculate the equilibrated pore spacing, we measured the distance between pore
-    centers.
-    \item Pore centers were located by averaging the coordinates of sodium ions in their 
-    respective pores.
-    \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
+%    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
+%    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
+%    resulting from a tightly packed initial configuration.
+%    \item To calculate the equilibrated pore spacing, we measured the distance between pore
+%    centers.
+%    \item Pore centers were located by averaging the coordinates of sodium ions in their 
+%    respective pores.
+%    \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
     	% Supplemental vvvv
-	\begin{itemize}
+%	\begin{itemize}
         %MRS2: make clear sampling what?
-        \item We are interested in 5 pore-to-pore distances which should all be equal in
-        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
-	\item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
-	the system is equilibrated, we calculate how long it takes for the data in each of the 5
-	trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
-	\item We break the full trajectories down into sub-trajectories based on the
-	maximum autocorrelation time of those found in the previous step. 
-    	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
-    	sampling pore spacings from the sub-trajectories 
-    	\item We get an average value for each pore spacing by finding the mean of the bootstrapped data
-	\item We calculate the overall average as the mean of all bootstrapped pore spacings
-	\item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
-	average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
-	\item We report the mean of these uncertainties
+%        \item We are interested in 5 pore-to-pore distances which should all be equal in
+%        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
+%	\item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
+%	the system is equilibrated, we calculate how long it takes for the data in each of the 5
+%	trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
+%	\item We break the full trajectories down into sub-trajectories based on the
+%	maximum autocorrelation time of those found in the previous step. 
+%    	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
+%    	sampling pore spacings from the sub-trajectories 
+%    	\item We get an average value for each pore spacing by finding the mean of the bootstrapped data
+%	\item We calculate the overall average as the mean of all bootstrapped pore spacings
+%	\item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
+%	average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
+%	\item We report the mean of these uncertainties
         % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
@@
         % Supplemental ^^^^
-	\end{itemize}
-  \end{itemize}
-
-  %MRS: pore radius is a different category isn't it? Is this an input piece of data?
-  % should be put in a different category.
-  %BJC: Well I still have to initially place the monomers some distance away from the pore
-  % centers. That distance is informed by the experimental evidence.
-
-%  We based the pore radii of our initial configuration on past TEM and size exclusion 
-%  rejection data
-%MRS2: maybe this fits somewhere else, since it's not really used in the same way - it's more descriptive.
-In fact, maybe better to say it WASN'T used at all to constrain initial choice, and we simply looked at it after to understand how the pore size is affected by other choices.
-Or maybe I'm still misunderstanding.
-
-  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
-  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
-  of pore radius in the initial configuration.
-  \begin{itemize}
-    \item Experimental evidence suggests uniform pores with radii of 0.6 nm 
-    \item Comparing a geometric measurement of pore size derived from an atomistic model,
-    to a less precise, experimentally derived pore size estimate, will give ambiguous results.
-    \item What is meant by pore radius will not be clear until we establish a clear picture
-    of the nanoscopic pore environment.
-    \item When constructing pores, we chose the carboxylate carbon from the monomer
-    head group as a reference atom, and placed it a distance r from the pore center,
-    where r is the pore radius (~\ref{fig:pore_radius_illustration}). % BJC: Figure in Supplemental Information?
-    \item We will not make direct comparisons of pore radius between our model 
-    and experiment to avoid the ambiguity, however, we do define a pore radius  
-    for our own purposes.
+%	\end{itemize}
+%  \end{itemize}
+
+% BJC: This can be covered more in the Supplmental ... it might not even be necessary. I won't
+% report any "pore sizes" except in the supplemental where I will show that the initial choice
+% of pore radius has little effect on pore size
+
+%  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
+%  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
+%  of pore radius in the initial configuration.
+%  \begin{itemize}
+%    \item Experimental evidence suggests uniform pores with radii of 0.6 nm 
+%    \item Comparing a geometric measurement of pore size derived from an atomistic model,
+%    to a less precise, experimentally derived pore size estimate, will give ambiguous results.
+%    \item What is meant by pore radius will not be clear until we establish a clear picture
+%    of the nanoscopic pore environment.
+%    \item When constructing pores, we chose the carboxylate carbon from the monomer
+%    head group as a reference atom, and placed it a distance r from the pore center,
+%    where r is the pore radius (~\ref{fig:pore_radius_illustration}). % BJC: Figure in Supplemental Information?
+%    \item We will not make direct comparisons of pore radius between our model 
+%    and experiment to avoid the ambiguity, however, we do define a pore radius  
+%    for our own purposes.
     %\item To measure the pore radius in our model we calculate the distance between 
@@
     %in their respective pores.
-  \end{itemize}
+%  \end{itemize}
 
 %MRS2: is the pore radius of the initial configuration really relevant? Does it need to be defined?  Seems like what radius means in the final equilibrated one is more important.
-%BJC: maybe not, we'll have to talk to get on the same page
-  \begin{figure}
- 	\centering
- 	\includegraphics[width=\textwidth]{pore_radius_illustration.png}
-	\caption{The pore radius of the initial configuration is defined using the 
-        carboxylate carbon as a reference}~\label{fig:pore_radius_illustration}
-  \end{figure}
+%BJC: This can go in supplemental
+%  \begin{figure}
+% 	\centering
+% 	\includegraphics[width=\textwidth]{pore_radius_illustration.png}
+%	\caption{The pore radius of the initial configuration is defined using the 
+%        carboxylate carbon as a reference}~\label{fig:pore_radius_illustration}
+%  \end{figure}
 
@@
     \item Both have reported stacking distances near the R-$\pi$ value of 3.7 \angstrom % Reference
-    \item Headgroups in the sandwiched configuration are stacked directly on top of
-    each other while stacked headgroups in the parallel displaced configuration are offset 
-    by $180/nmon$ degrees where $nmon$ equals the number of monomers per layer.
+    \item Headgroups in our sandwiched initial configuration are stacked directly
+    on top of each other while stacked headgroups in the parallel displaced 
+    initial configuration are offset by $180/nmon$ degrees where $nmon$ equals
+    the number of monomers per layer.
     %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
@@
 
-%MRS2: seems like the number per layer might be listed here, since that was adjusted during the fitting process?
-Hmm.
-I see it's later in the results.
-It's a bit confusing what variables are listed here (initial geometry settings), and what is discussed in the results section.
-(like number per layer)  We should discuss.
-
-  %We tested a number of equilibration schemes of increasing complexity in an effort
-  %to match experiment while overcoming kinetic limitations that might trap the system 
-  %in a metastable states. All start from an initial configuration generated with 
-  %chosen structure variables.
+  As outlined in \ref{point:monomernum} the number of monomers in each layer is unknown
+  so we tested configurations constructed with a varied number of monomers per layer.
+  \begin{itemize}
+	\item Systems were built in the offset and parallel displaced configurations
+        with 4, 5, 6, 7 and 8 monomers per layer
+  \end{itemize}
+
+  %%%%%%%%%%%% Equilibration %%%%%%%%%%%%%%
+
   We developed equilibration schemes to create dry and wet configurations. Both schemes 
@@
 	  \item In order to create a wet system, we solvated an initial configuration with water using gmx solvate
-          \item All waters placed outside the pore region are removed 
+          \item All water molecules placed outside the pore region are removed 
 	  \item Waters inside the pore region are randomly removed until the desired concentration
@@
 
-  % BJC: To be replaced by Joe's description
-  Simulated X-ray diffraction patterns were generated based on atomic
-  coordinates for a direct experimental comparison.
-  \begin{itemize}
-    \item All atomic coordinates were simulated as gaussian spheres of electron
-    density corresponding to each atom's atomic number.
-    \item A three dimensional fourier transform (FT) of the array of electron 
-    density results in a three dimensional structure factor which represents
-    the unit cell in reciprocal space.
-   % \item We perform an angular average of the structure factor about the 
-    z axis to generate a 2D cross section close to what one would see 
-    experimentally.
-    \item We matched experimental 2D WAXS patterns by adjusting the initial 
-    spacing between layers and the orientation of the head groups with respect
-    to adjacent layers.
-  \end{itemize}
-
-  \begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{}\label{fig:sandwiched}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{PD.png}
-		\caption{}\label{fig:pd}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{}\label{fig:tshaped}
-	\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwichedlayers.png}
-		\caption{}\label{fig:sandwichedlayers}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{offsetlayers.png}
-		\caption{}\label{fig:offsetlayers}
-	\end{subfigure}
-	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
-	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
-	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
-	configuration }\label{fig:stacking}
-  \end{figure}
-
-  We calculated ionic conductivity using two different methods for robustness.
-  \begin{itemize}
-    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
-    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
-    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
-    \item Sodium ion diffusion coefficients were found by calculating the slope
-    of the linear region of the z-direction mean square displacement curve as indicated by
-    the einstein relation \cite{einstein_investigations_1956}.]
-    %MRS: state how you decided which was the linear region.
-    %BJC: nothing fancy other than looking at the msd plot and determining where to
-    % start fitting. I suppose I could minimize R^2 but that seems like overkill
-    \item We looked at the MSD plot to determine where to begin and end a linear fit
-    \item Ion concentration was measured with respect to the entire unit cell. 
-    % new paragraph
-    \item The second method, termed the 'Collective Diffusion' model, measures 
-    the movement of the collective variable, Q, which is defined as the amount
-    of charge transfer through the system and can be thought to represent
-    the center of charge of the system.
-    \item The conductance, $\gamma$ of the system can be calculated as:
-    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
-    achieved by multiplying by channel length and dividing by the membrane
-    cross sectional area.
-    \item $D_Q$ is the diffusion coefficient of the collective variable Q. It can
-    be calculated using the einstein relation.
-    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
-  \end{itemize}
+%%%%%%%%%%%%% Crosslinking %%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%% Equilibrium Calculations %%%%%%%%%%%%%%%
+
+  Using equilibrated structures, we carry out various calculations to characterize the
+  system. 
+  \begin{itemize}
+	\item We determine the point at which a system is equilibrated when the 
+        distance between pores stops changing
+  \end{itemize}
+
+  To calculate the equilibrated pore spacing, we measured the distance between pore
+  centers.
+  \begin{itemize}
+	\item Pore centers were located by averaging the coordinates of sodium ions in their
+	respective pores.
+	\item Statistics were generated using the bootstrapping technique (See Supplemental Information)
+	% Supplemental vvvv
+        \begin{itemize}
+        	%MRS2: make clear sampling what?
+	        \item We are interested in 5 pore-to-pore distances which should all be equal in
+	        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
+	        \item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
+	        the system is equilibrated, we calculate how long it takes for the data in each of the 5
+	        trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
+	        \item We break the full trajectories down into sub-trajectories based on the
+	        maximum autocorrelation time of those found in the previous step.
+	        \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly
+	        sampling pore spacings from the sub-trajectories
+	        \item We get an average value for each pore spacing by finding the mean of the bootstrapped data
+	        \item We calculate the overall average as the mean of all bootstrapped pore spacings
+	        \item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
+	        average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
+	        \item We report the mean of these uncertainties
+	        % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
+	        % BJC: Updated
+        \end{itemize}
+        % Supplemental ^^^^^
+  \end{itemize}
+
+  To quantify the degree of layering and the equilibrium distance between layers
+  in our system, we calculate a spatial correlation function, $g(z)$, measured
+  along the z-axis (perpendicular to the membrane plane).
+  \begin{itemize}
+    \item To calculate $g(z)$, we binned the z component distances between
+    the center of mass of each component and all others of the same pore
+    over at least 50 ns of equilibrated trajectory and then normalized by the 
+    average number density.
+%    \item We compare the degree of layering between systems based on the
+%    amplitude of the first peak in $g(z)$. We halve the difference between the
+%    maximum of the first peak and the following minimum. We compare the difference
+%    to the mean to get a percentage deviation from the average number density.
+    \item To extract the average distance between layers we applied a discrete
+    fourier transform to $g(z)$ and extracted the highest intensity frequency
+  \end{itemize}
+
+  % BJC: To be replaced by Joe's description
+  Simulated X-ray diffraction patterns were generated based on atomic
+  coordinates for a direct experimental comparison.
+  \begin{itemize}
+    \item All atomic coordinates were simulated as gaussian spheres of electron
+    density corresponding to each atom's atomic number.
+    \item A three dimensional fourier transform (FT) of the array of electron 
+    density results in a three dimensional structure factor which represents
+    the unit cell in reciprocal space.
+   % \item We perform an angular average of the structure factor about the 
+    z axis to generate a 2D cross section close to what one would see 
+    experimentally.
+    \item We matched experimental 2D WAXS patterns by adjusting the initial 
+    spacing between layers and the orientation of the head groups with respect
+    to adjacent layers.
+  \end{itemize}
+
+  % BJC: I think this figure belongs somewhere else
+  \begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{sandwiched.png}
+		\caption{}\label{fig:sandwiched}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{PD.png}
+		\caption{}\label{fig:pd}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Tshaped.png}
+		\caption{}\label{fig:tshaped}
+	\end{subfigure}
+	\vskip\baselineskip
+	\begin{subfigure}[b]{0.475\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{sandwichedlayers.png}
+		\caption{}\label{fig:sandwichedlayers}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.475\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{offsetlayers.png}
+		\caption{}\label{fig:offsetlayers}
+	\end{subfigure}
+	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
+	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
+	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
+	configuration }\label{fig:stacking}
+  \end{figure}
+
+  We explored the pore composition by measuring the average number densities of
+  various monomer components with respect to the pore centers.
+  \begin{itemize}
+	\item The centers of the pores were located using the same method to
+        calculate the equilibrium pore spacing
+        \item We looked at the average number density of sodium ions, aromatic
+	rings and carbon atoms making up the monomer tails 
+	\item The radial distance from the pore center of all atoms in each group
+        are binned then normalized by area 
+	% Maybe write an equation here? It's hard to say precisely how I did it in words without it sounding confusing 
+  \end{itemize}
+
+  We calculated ionic conductivity using two different methods for robustness.
+  \begin{itemize}
+    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
+    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
+    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
+    \item Sodium ion diffusion coefficients were found by calculating the slope
+    of the linear region of the z-direction mean square displacement curve as indicated by
+    the einstein relation \cite{einstein_investigations_1956}.]
+    %MRS: state how you decided which was the linear region.
+    %BJC: nothing fancy other than looking at the msd plot and determining where to
+    % start fitting. I suppose I could minimize R^2 but that seems like overkill
+    \item We looked at the MSD plot to determine where to begin and end a linear fit
+    \item Ion concentration was measured with respect to the entire unit cell. 
+    % new paragraph
+    \item The second method, termed the 'Collective Diffusion' model, measures 
+    the movement of the collective variable, Q, which is defined as the amount
+    of charge transfer through the system and can be thought to represent
+    the center of charge of the system.
+    \item The conductance, $\gamma$ of the system can be calculated as:
+    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
+    achieved by multiplying by channel length and dividing by the membrane
+    cross sectional area.
+    \item $D_Q$ is the diffusion coefficient of the collective variable Q. It can
+    be calculated using the einstein relation.
+    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
+  \end{itemize}
+
   \section*{Results and Discussion}
@@
         Supplemental Information.  %BJC: "Power spectrum" an okay description here?
+	% BJC: TODO: Overlay plots of tail and headgroup densities
         %MRS2: repore more precisely what finding is interesting. What does that difference mean?
-	\item We see a difference in the spacing in the head group versus tail region
-	because there is more volume to fill with less densely packed carbon chains in the tail region. 
+%	\item We see a difference in the spacing in the head group versus tail region
+%	because there is more volume to fill with less densely packed carbon chains in the tail region. 
 	% BJC: vvv Need to get the same information for the tail zdfs.
-	\item Even though the layer spacing is similar, the sandwiched configuration
-	exhibits more defined layers with its first peak deviating from the mean 
-        number density by 61 \%. %BJC: I mention how I do this calculation in the methods. Is it clear that I'm doing that here?
+%	\item Even though the layer spacing is similar, the sandwiched configuration
+%	exhibits more defined layers with its first peak deviating from the mean 
+%        number density by 61 \%. %BJC: I mention how I do this calculation in the methods. Is it clear that I'm doing that here?
 %MRS2: fine for description for now.          
-	\item The parallel displaced configuration deviates from the mean by only 
-	12 \% in comparison.
+%	\item The parallel displaced configuration deviates from the mean by only 
+%	12 \% in comparison.
 %MRS2: is this that unexpected, since parallel displaces should have layers that alternate anyway?
@@
 %  \end{table}
-
-%  To answer question (3) we require high resolution experimental evidence which we 
-%  can match to our simulations. Experimental WAXS measurements encode all structural
-%  details and we would like to match them as well as possible. 
-%  %MRS: also encodes the pore spacing
-%  %BJC: got rid of 'remaining' in 'remaining structural details'
-%  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
-%  \begin{itemize}
-%  	\item There are five major features present in the 2D experimental 
-%	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
-%	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
-%	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
-%	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-%	perpendicular to the membrane plane, or z-axis. For simplicity, this 
-%	reflection will be referred to as R-$\pi$.
-%       %MRS: why R in R-pi? for reflection?
-%	%BJC: yes, R = reflection
-%	\item A weak intensity line is located at exactly half the $q_z$ value of
-%	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
-%	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
-%	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
-%	along the z axis meaning if the positions of the aromatic rings can
-%	be traced by a helix, then for each turn in the helix, there should be
-%	two aromatic rings. For this reason it will be referred to as R-helix.
-%	\item A third major reflection is marked by a low intensity ring located
-%	at r = 1.4 \angstrom$^-1$. The real space separation 
-%	corresponds to 4.5 \angstrom~ which is characteristic of the average 
-%	spacing between packed alkane chains. This reflection will be called R-alkanes.
-%	\item Within R-alkanes, are four spots of higher intensity which 
-%	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
-%	in their respective quadrants. In many liquid crystal systems this can be
-%	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
-%	\item The final major reflections correspond to the spacing and symmetry of 
-%	the d\textsubscript{100} plane which can be related to the distance between
-%	pores. The feature, which will be called R-pores, is characterized by dots 
-%	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
-%	symmetry of the packed pores. It is easiest to interpret the data by 
-%	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
-%  \end{itemize}
-
-%  \begin{figure}[!ht]
-%	\centering
-%	\begin{subfigure}[t]{0.47\linewidth}
-%		\centering
-%		\raisebox{.2\textwidth}{%
-%		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
-%		}
-%		\caption{}\label{fig:WAXS}
-%	\end{subfigure}
-%	\begin{subfigure}[t]{0.43\linewidth}
-%		\centering
-	%	\vspace{12mm}
-%		\includegraphics[width=\linewidth]{SAXS.png}
-%		\caption{}\label{fig:SAXS}
-%	\end{subfigure}
-%	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
-%	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
-%	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
-        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
-	%BJC: 1D is from a Yale paper. I'm going to remake the figure from the raw data but will reference that
-	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
-%  \end{figure}
-
-%BJC: metastable stuff
-%  The $z$-direction correlation functions show that layers in our model prefer
-%  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
-%  with layers stacked 4.0 nm apart and to our surprise, we observed
-%  long-term stability of a qualitatively different configurations suggesting
-%  that we have found more than one metastable free energy basin.
-%  %that the initial distance between layers can influence the approach towards 
-%  %equilibrium.
-%  \begin{itemize}
-%  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
-%        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
-%	structure.
-%        \item We will refer to this large set of configurations, with an open pore, as 
-%        the OP Basin (open pore) (Figure~\ref{fig:OPbasin}).
-%	\item Simulations of systems built with layers stacked greater than 4 
-%	\angstrom~ apart results in a pore structure characterized by high radial 
-%	disorder, while still maintaining partitioning between hydrophobic and 
-%	hydrophilic regions.
-%	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:CPbasin}).
-%	\item This LLC membrane may exist in at least two metastable states.
-%	\item The distinct difference in pore structure exhibited by each phase will 
-%	likely lead to different transport mechanisms.
-%	\item Because the pore structure will vary between each Basin, understanding 
-%	which phase exists experimentally is necessary in order to ensure we are 
-%	studying the system which actually dominates.
-%  \end{itemize}
-
-%  \begin{figure}[!ht]
-%        \centering
-%        \begin{subfigure}[b]{0.475\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-%                \caption{}\label{fig:OPbasin}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.475\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
-%                \caption{}\label{fig:CPbasin}
-%        \end{subfigure}
-%	\caption{From a qualitative standpoint, the OP Basin (a) is characterized by a
-%	hollow cylindrical pore while pores in the CP Basin (b) are characterized by a
-%	higher degree of radial disorder}\label{fig:basins}
-%  \end{figure}
 
@@
 
+  The $z$-direction correlation functions show that layers in our model prefer
+  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration
+  with layers stacked 5.0 nm apart and to our surprise, we observed
+  long-term stability of a qualitatively different configuration suggesting
+  that we have found more than one metastable free energy basin, corroborating \ref{point:metastable}.
+  %that the initial distance between layers can influence the approach towards 
+  %equilibrium.
+  \begin{itemize}
+        \item Equilibrated systems built according to the 3.7 \angstrom~layer spacing
+        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore
+        structure.
+        \item We will refer to this large set of configurations, with an open pore, as
+        the ordered pore basin open pore (Figure~\ref{fig:OPbasin}).
+        \item Simulations of systems built with layers stacked 5
+        \angstrom~ apart results in a pore structure characterized by high radial
+        disorder, while still maintaining partitioning between hydrophobic and
+        hydrophilic regions.
+        \item This will be called the disordered pore basin (Figure~\ref{fig:DPbasin}).
+        \item This LLC membrane may exist in at least two metastable states.
+        \item The distinct difference in pore structure exhibited by each phase will
+        likely lead to different transport mechanisms.
+        \item Because the pore structure will vary between each Basin, understanding
+        which phase exists experimentally is necessary in order to ensure we are
+        studying the system which actually dominates.
+  \end{itemize}
+
+  \begin{figure}[!ht]
+        \centering
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+                \caption{}\label{fig:OPbasin}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
+                \caption{}\label{fig:DPbasin}
+        \end{subfigure}
+        \caption{From a qualitative standpoint, the ordered pore basin (a) is characterized by a
+        hollow cylindrical pore while pores in the disorder pore basin (b) are characterized by a
+        higher degree of radial disorder}\label{fig:basins}
+  \end{figure}
+
+  % INSERT XRD of disordered basin
+
+  In order to address \ref{point:poredefinition} and to further understand the structural difference 
+  between the ordered pore and disordered pore basins, we plotted the number of densities of
+  heavy atoms in the head group and tail regions of the monomers in addition to the sodium ions.
+  (See Supplemental Information for definition of head group and tail regions) 
+  \begin{itemize}
+	\item For the hydrophilic region, we used the carbon atoms making up the aromatic ring
+	\item For the hydrophobic components we used all carbon atoms of the monomer tails
+  \end{itemize}
+
+  % BJC: I'm not sure what to make of this figure right now. The parallel-displaced configuration shares
+  % more with the disordered pore phase
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.55\textwidth}
+        \includegraphics[width=1\linewidth]{offset_density.png}
+        \caption{}
+        \label{fig:offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.55\textwidth}
+        \includegraphics[width=1\linewidth]{layered_density.png}
+        \caption{}
+        \label{fig:offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.55\textwidth}
+        \includegraphics[width=1\linewidth]{disordered_density.png}
+        \caption{}
+        \label{fig:offset_density}
+  \end{subfigure}
+  \caption{(a) Parallel Displaced (b) Sandwiched (c) "Disordered"}~\label{fig:densities}
+  \end{figure}
+
   We answer (\ref{point:water}) and further support (\ref{point:orientation}) by preparing parallel displaced and

### 2017-12-01 HII/Scripts/equil.sh

@@ -12,7 +12,7 @@ forces="3162 56 8 3 2 1 0"
 MPI="off"
 NP=4
 T=300
-equil_length=100000  # equilibrium simulation length
+equil_length=1000000  # equilibrium simulation length
 solvate=0
 
 while getopts "b:x:y:z:r:m:t:p:f:e:s:S:" opt; do
@@ -56,7 +56,7 @@ fi
 
 cp npt.gro 1000000.gro
 cp npt.trr 1000000.trr
-exit
+
 input.py --mdp -b ${BUILD_MON} -l 50 --restraints --temp ${T} -f 50 --genvel no  -c ${start_config} # use velocities from previous sim
 
 for f in ${forces}; do
@@ -71,14 +71,14 @@ for f in ${forces}; do
 	cp npt.gro ${f}.gro
 	cp npt.trr ${f}.trr
 done
-exit
+
 #input.py --mdp -b ${BUILD_MON} -l 20000 --restraints --temp ${T} -f 50 --genvel no  # use velocities from previous sim
 #gmx grompp -f npt.mdp -p topol.top -c npt.gro -o wiggle
 input.py -b ${BUILD_MON} -l 5000 --temp ${T} -f 50 --barostat berendsen --genvel no # put pressure control back on
 gmx grompp -f npt.mdp -p topol.top -c 0.gro -o wiggle # run it out for a bit
 gmx mdrun -v -deffnm wiggle
 
-input.py -b ${BUILD_MON} -l ${equil_length} --temp ${T} -f 100 --barostat Parrinello-Rahman --genvel no
+input.py -b ${BUILD_MON} -l ${equil_length} --temp ${T} -f 1000 --barostat Parrinello-Rahman --genvel no
 gmx grompp -f npt.mdp -p topol.top -c wiggle.gro -o wiggle
 #analysis.sh # get pore spacing, thickness, pore size, convert the trajectory to be used in XrayDiffraction.exe
 

### 2017-12-05 Ben_Manuscripts/structure_paper/Outline.tex
Minor comments?
comments on latest outline.

@@
 % defined than the other. What is the right word for that? unambiguous? explicit?
+%MRS3: hmm.  Maybe look and see what other people call them when describing NF membranes.
     \item Larger and well-defined pores drive down energy requirements while
@@
     \item The choice of head group may allow us to tune pore size for size exclusion driven separations
+%MRS3: choice of counterion also affects size.  Counterion type probably doesn't affect Donnan potential that much IRCC, more the total amount of counterion.
     \item Choice of counterion may influence the establishment of a Donnan potential
@@
   %BJC: Okay. The picture here is of the "ordered pore" phase. It looks disorderd from this angle. I could use a different slice of the membrane to see if it looks any better
+%MRS: if this is ordered, OK.  Maybe could try to rotate it a bit more towards the reader.
   \begin{figure}
@@
   experiment cannot definitively answer. There are several key
-  questions that we intend to answer which will be laid out and numbered
+  questions that we intend to answer 
+%MRS3: we can't ``answer'' for sure, since it's a model, and may omit things.
+Could put ``several key questions we will investigate'' or ``hope to provide evidence for or against'', or something like that.
+which will be laid out and numbered
   in subsequent paragraphs.
@@
 I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).
-
 %MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems.
@@
   into stacked layers which form columnar pores. There has been no definitive
-  answer in literature regarding the number of monomers in each layer. We want to
+  answer in literature regarding the number of monomers in each layer. 
+%MRS3: the intro to the list talks about only ``numbers of monomers in each layer'', whereas the list below talks about several questions relating to layers.
+Can you rephrase so it's more general?
+Maybe just take out that sentence above.
+We want to
   know 
@@
 	\item While the Col\textsubscript{h} phase is described as dry, it is 
+          %MRS3: ``possible'' -> likely, and give some explanations why we think likely?
 	possible that small amounts of ambient water may be leached into the system.
@@
     \item A second system is explored with an initial layer spacing of 5 \angstrom
+%MRS3: at least state in the main body what went wrong with it in a sentence or so, with details in supplemental. 
    \item A third system with an initial layer spacing of 10 \angstrom was briefly
@@
 	%BJC: I've never explored whether there is any dependence on initial force constant. It probably doesn't matter unless it starts really low
+        %MRS3: then just state what you did, so it could be repeated. 
           \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
@@
 	        \item We calculate the overall average as the mean of all bootstrapped pore spacings
+                  %MRS3: this sounds a little convoluted below.  Should just be the standard error in the boostrap estimates of the pore spacing?
+                  %MRS3: this can be fixed in the draft not outline.
 	        \item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
@@
 	\end{subfigure}
+%MRS: 
   \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
@@
 %BJC: That's good! One is angles measured between tail centroids and the other is radial integration of the simulated xrd patterns. I'll try make that more clear in the caption.
+%MRS3: sorry, I meant to say not clear what the SOURCE of the data is in right vs. left.  Make sure colors and labels are consistent in final 
+%MRS: not clear why some are angles with x axis, and some are angles w neighbors?  Shouldn't it be the same thing plotted in both graphs?
   \end{figure}
@@
         hydrophilic regions.
+ %MRS3: need to address the similar RDFs.
+What data can show they are different?
+Or maybe they HAVE rdfs, but not good layering?
+Have you done the fourier transform on them?
+We can still rule them out based on the XRD, of course.
+But surprising the same RDFs.
         \item This will be called the disordered pore basin (Figure~\ref{fig:DPbasin}).
@@
         likely lead to different transport mechanisms.
-        \item Because the pore structure will vary between each Basin, understanding
+        \item Because the pore structure will vary between each basin, understanding
         which phase exists experimentally is necessary in order to ensure we are
@@
         higher degree of radial disorder}\label{fig:basins}
+%MRS3: see note on RDF.
   \end{figure}
@@
   % more with the disordered pore phase
+  % MRS3: yeah, see my notes on this.  wE need to understand how it can be visually open, and still have this structure.  
+  % doesn't this structur have a different pore-to-pore distance.
   \begin{figure}
@@
   \end{subfigure}
-  \caption{(a) Parallel Displaced (b) Sandwiched (c) "Disordered"}~\label{fig:densities}
+  \caption{(a) Parallel Displaced (b) Sandwiched (c) ``Disordered''}~\label{fig:densities}
   \end{figure}
+
+%MRS3: this needs a caption, and need to write some text analyzing it.
+The thing that throws me off is that the RDF's look about the same for parallel displaced and disordered!
+That's pretty hard to rationalize with the idea that the pores are open vs.
+closed.
+What am I missing?
+Very interesting regardless!
 
@@
 
+%MRS3: is this point the right ``main'' thesis to make?
+I thought it was a more simple statement of being interested as to how water affected the structure.
+FYI, would be interesting to see the RDF's of the pores with and without water, BUT I think that's not necessary for this paper, that's more a 2nd paper thing.
+%MRS3: we didn't really test if water is  needed to obtain the structures; clearly, w/o water it's metastable for a long time.  We don't need the water simulations to prove this.  
   Water is not needed to obtain and simulate the correct equilibrium 
@@
 % it'd be clearer that way since but maybe it's not?
+%MRS3: state more clearly in the caption why you are showing it. i.e. ``this data shows that pores in the system are somewhat tortuous'', then explain how the figure shows that.
   \caption{The experimental two dimensional SAXS pattern exhibits reflections
@@
 	the parallel-displaced configuration produces a structure with the closest match to experiment.
+%MRS3: water is not needed to create well-defined pore structures?  I'm not sure ``maintain'' is the right word, and ``membrane structure'' may be too vague.
 	\item Finally, water is not needed to maintain membrane structure our data 

### 2017-12-06 Ben_Manuscripts/structure_paper/Draft.tex
Turning outline into draft - intro text nearly done

--- 2017-12-05 Ben_Manuscripts/structure_paper/Outline.tex
@@
 \usepackage{float}
-\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
+\usepackage{setspace}
+\doublespacing
+
+\title{Understanding the nanoscale structure of hexagonal phase
+lyotropic liquid crystal membranes}
+\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble
+\and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R.
+Shirts}
+
 \begin{document}
+
   \bibliographystyle{ieeetr}
@@
   \maketitle
+
   \section*{Introduction}
@@
   Nanostructured membrane materials have become increasingly popular for
-  aqueous separations applications such as desalination and biorefinement
-  because they offer the ability to control membrane architecture at the
-  atomic scale allowing the design of solute-specific separation membranes. \cite{humplik_nanostructured_2011}
-  \begin{itemize}
-    \item Most membrane-based aqueous separations of small molecules can 
-    be achieved using reverse osmosis (RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}
-  \end{itemize}
-
-  While RO and NF have seen many advances in the past few decades, they 
-  are far from perfect separation technologies.
-  \begin{itemize}
-    \item \textit{RO membranes}
-    \item Inconsistent performance : Current state-of-the-art RO membranes are unstructured with
-    tortuous and polydisperse diffusion pathways which leads to 
-    inconsistent performance \cite{song_nano_2011}
-    \item High energy requirements : Necessarily high feed pressures 
-    drive up energy requirements which strains developing regions and
-    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
-    \item Separation based on differences in solubility and diffusivity:
-%MRS2: couldn't you argue that the fact that they diffuse and dissolve at different rates means that it makes it possible to design targeted separations?
-%BJC: right, I say something like that in the sentence following this one. It would be more challenging to design a targeted separation 
-% especially if the feed is complex
-    Moreover, designing RO membranes to achieve targeted separations of 
-    specific solutes in a complex feed solution is nearly impossible because various solutes dissolve
-    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
-    \item With optimization, one can exploit these differences to create a functional
-    selective barrier.
-    \item \textit{NF membranes}
-    \item NF was introduced as an intermediate between RO and ultrafiltration,
-    having the ability to separate organic matter and salts on the order of 
-    one nanometer in size.
-%MRS2: is ``well-defined'' the right word if there is a ``pore size distribution''?
-%BJC: By well-defined, I'm thinking of cylinders versus polymer matrix. One is definitely more
-% defined than the other. What is the right word for that? unambiguous? explicit?
-%MRS3: hmm.  Maybe look and see what other people call them when describing NF membranes.
-    \item Larger and well-defined pores drive down energy requirements while
-    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
-    \item NF is often used as a precursor to reverse osmosis
-    \item Unfortunately, NF membranes, like RO, possess a pore size 
-    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
-  \end{itemize}
+  aqueous separations applications such as desalination and biorefinement because
+  they offer the ability to control membrane architecture at the atomic scale
+  permitting the design of solute-specific separation membranes.
+  \cite{humplik_nanostructured_2011} Most membrane-based aqueous separations of
+  small molecules can be achieved using reverse osmosis (RO) or nanofiltration
+  (NF). \cite{van_der_bruggen_review_2003}
+
+  While RO and NF have seen many advances in the past few decades, they are far
+  from perfect separation technologies. Current commericial RO membranes are thin
+  film composite membranes with a porous support layer and an active layer made
+  of a dense polyamide polymer matrix.  The membranes are unstructured with
+  tortuous and polydisperse diffusion pathways. Separation occurs as solutes
+  dissolve into and diffuse through voids in the polymer matrix at different
+  rates.\cite{wijmans_solution-diffusion_1995} With optimization, one can exploit
+  these differences to create a functional selective barrier. High feed pressures
+  are required in order to achieve economical solvent flux. The largest
+  application of reverse osmosis is desalination. A typical seawater desalination
+  process requires feed pressures in the range of 800 to 1000 psi in order to
+  overcome osmotic pressure. \cite{fritzmann_state---art_2007} Only 0.5 \% of the
+  world's water is fresh. Desalination is an important source of potable water,
+  necessary in order to keep up with demand generated by a rapidly growing global
+  population. Although RO is currently the cheapest form of desalination, the
+  cost must be further decreased in order to meet demand. By designing better
+  membranes for desalination, we can achieve higher water fluxes and lower feed
+  pressure requirements which will decrease the cost of fresh water production.
+  \cite{humplik_nanostructured_2011}.
+
+  % financially straining developing regions and contributing strongly to
+  % CO\textsubscript{2} emissions. \cite{mcginnis_global_2008} Moreover,
+  % designing RO membranes to achieve targeted separations of specific solutes
+  % in a complex feed solution is nearly impossible
+
+  NF was introduced as an intermediate between RO and ultrafiltration, having
+  the ability to separate organic matter and salts on the order of one nanometer
+  in size. Explicit pore pathways running through the thickness of the membrane
+  permit high solvent fluxes at lower pressures than RO. NF membranes typically
+  have a surface charge resulting from ionizable groups which affords separation
+  of ions smaller than the pore readius by Donnan exclusion.
+  \cite{van_der_bruggen_review_2003} NF is often used as a precursor to reverse
+  osmosis since it can efficiently remove a significant portion of dissolved
+  solutes. Following NF pretreatment, RO can further purify the permeate at lower
+  pressure. Unfortunately, NF membranes, like RO, possess a pore size
+  distribution which limits their ability to perform precise separations
+  \cite{bowen_modelling_2002}. An NF membrane with high selectivity could offer
+  the versatility to separate ions as well as small charged and uncharged
+  molecules to the same degree as RO and at a significantly lower cost.
 
   Nanostructured membranes can bypass many of the performance issues which
-  plague traditional NF and RO membranes.
-  \begin{itemize}
-    \item Tune size and functionality of building blocks to control pore
-    size and shape: One can accomplish targeted separations with high 
-    selectivity by tuning shape, size and functionality of the molecular
-    building blocks which form these materials. 
-    \item As a result, solute rejecting pores can have their sizes tuned
-    uniformly, resulting in strict size cut-offs.
-    \item Entirely different mechanisms may govern transport in a given
-    nanostructured material which can inspire novel separation techniques.
-  \end{itemize}
-
-  Development of nanostructured materials has been limited by the ability
-  to synthesize and scale various fundamentally sound technologies.
-  \begin{itemize}
-    \item Graphene sheets are atomically thick which results in excellent
-    permeability but defects during manufacturing severely impact 
-    selectivity. \cite{cohen-tanugi_multilayer_2016}
-    \item Molecular dynamics simulations of carbon nanotubes show
-    promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
-    unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
-    \item Zeolites have sub-nm pores with a narrow pore size 
-    distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
-    however, experimental rejection was low and attributed to interstitial
-    defects formed during membrane synthesis \cite{li_desalination_2004}
-    \item There is a need for a scalable nanostructured membrane
-  \end{itemize}
+  plague traditional NF and RO membranes. One can accomplish targeted separations
+  with high selectivity by tuning shape, size and functionality of the molecular
+  building blocks which form these materials. As a result, solute rejecting pores
+  can have their sizes tuned uniformly, resulting in strict size cut-offs.
+  Entirely different mechanisms may govern transport in a given nanostructured
+  material which can inspire novel separation techniques.
+
+  Development of nanostructured materials has been limited by the ability to
+  synthesize and scale various fundamentally sound technologies.  Graphene sheets
+  are atomically thick which results in excellent water permeability but defects
+  during manufacturing severely impact selectivity.
+  \cite{cohen-tanugi_multilayer_2016} Molecular dynamics simulations of carbon
+  nanotubes show promise \cite{humplik_nanostructured_2011} but synthetic
+  techniques are unable to achieve scalable alignment and pore monodispersity.
+  \cite{hata_water-assisted_2004,maruyama_growth_2005} Zeolites have sub-nm pores
+  with a narrow pore size distribution and MD simulations exhibit complete
+  rejection of solvated ions, \cite{murad_molecular_1998} however, experimental
+  rejection was low and attributed to interstitial defects formed during membrane
+  synthesis. \cite{li_desalination_2004} There is a need for a scalable
+  nanostructured membrane.
 
   Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
-  aqueous separation applications. 
-  \begin{itemize}
-    \item LLCs share the characteristic ability of nanostructured membrane
-    materials to create highly ordered structures with the added benefits
-    of low cost and synthetic techniques feasible for 
-    large scale production \cite{feng_scalable_2014}
-    \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-    phase. The presence of water results in the H\textsubscript{II} phase.
-    \item In both cases, monomers assemble into mesophases made of hexagonally
-    packed, uniform size, cylinders with hydrophilic groups oriented inward
-    towards the pore center and hydrophobic groups facing outward.
-    \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
-    the monomer named Na-GA3C11 have been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
-    zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
-  \end{itemize}
-
-  Research into LLC membranes has been revived in recent years.
-  \begin{itemize}
-    \item During early stages of exploration, mesophases formed by Na-GA3C11 could not be macroscopically
-    aligned, resulting in low flux membranes, and no clear route towards 
-    scalable and economical filtration. 
-    \item In 2014, Feng et al. showed that the mesophases could be aligned 
-    using a magnetic field with subsequent crosslinking to lock the structure
-    in place \cite{feng_scalable_2014}
-    \item In 2016, Feng et al. showed that the same result could be obtained 
-    using a technique termed soft confinement \cite{feng_thin_2016}.
-  \end{itemize}
+  aqueous separation applications. LLCs share the characteristic ability of
+  nanostructured membrane materials to create highly ordered structures with the
+  added benefits of low cost and synthetic techniques feasible for large scale
+  production.  \cite{feng_scalable_2014} LLC systems created by the monomer named
+  Na-GA3C11 have been extensively studied experimentally.
+  \cite{smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}
+  Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h} phase.
+  The presence of ca. 10 wt \% water results in the H\textsubscript{II} phase. In
+  both cases, monomers assemble into mesophases made of hexagonally packed,
+  uniform size, cylinders with hydrophilic head groups oriented inward towards
+  the cylinder center.  The hydrophilic region can act as a pore for aqueous
+  separations.  One can envision tailoring the pore region for specific
+  separations by changing the monomer chemsitry.
+
+  Research into LLC membranes has been revived in recent years.  During early
+  stages of exploration, mesophases formed by Na-GA3C11 could not be
+  macroscopically aligned, resulting in low flux membranes, and no clear route
+  towards scalable and economical filtration. In 2014, Feng et al. showed that
+  the mesophases could be aligned using a magnetic field with subsequent
+  crosslinking to lock the structure in place. \cite{feng_scalable_2014} In 2016,
+  Feng et al. showed that the same result could be obtained using a technique
+  termed soft confinement. \cite{feng_thin_2016}
 
   % BJC: Not sure this figure needs to be in the paper. 
-  %MRS2: good question.  It helps give people context, which is necessary to move forward.  Perhaps 
-  %leave it in for now, though may need to get permission to reprint it.
-  \begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{soft_confinement.png}
-	\caption{The wedge shaped liquid crystal monomer (a) self assembles into 
-	mesophases with hexagonally packed pores (b). The pores are made of 
-	stacked monomer disks. A sub-micron-thick film is created by casting a 
-	dilute solution of Na-GA3C11/THF solution onto a silicon substrate and 
-	and allowing the solvent to evaporate. The thin film contains nanoporous 
-	columns which lie parallel to the film plane. (d) When a soft PDMS pad is 
-	imposed to the thin film, with subsequent thermal annealing, the columns
-	align perpendicular to the film plane. (e) Photo-cross-linking of the
-	aligned film creates a mechanically stable thin film with vertically 
-	aligned nanopores}~\label{fig:soft}
-  \end{figure}
-
-  A molecular level understanding of LLC membrane structure, enabled by molecular
-  dynamics simulations, will provide guidelines to reduce the large chemical space
-  available to design monomers for creation of separation-specific membranes.
-  \begin{itemize}
-    \item Over the past 20 years, H\textsubscript{II} phase LLC membrane studies have been limited primarily
-    to Na-GA3C11 with some characterization done after minor structural modifications
-    \item Resel et al. varied the length of the monomer tails and the counterion used and 
-    observed its affect on pore spacing \cite{resel_structural_2000}.
-    \item Rejection studies show that this membrane can not perform separations of
-    solutes less than 1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
-    \item  We do not yet understand how to controllably reduce the effective pore size or 
+  %MRS2: good question.  It helps give people context, which is necessary to
+  %move forward.  Perhaps leave it in for now, though may need to get
+  %permission to reprint it.
+  \begin{figure} \centering
+  \includegraphics[width=\linewidth]{soft_confinement.png} \caption{The wedge
+	  shaped liquid crystal monomer (a) self assembles into mesophases with
+		  hexagonally packed pores (b). The pores are made of stacked monomer disks. A
+		  sub-micron-thick film is created by casting a dilute solution of Na-GA3C11/THF
+		  solution onto a silicon substrate and and allowing the solvent to evaporate.
+		  The thin film contains nanoporous columns which lie parallel to the film plane.
+		  (d) When a soft PDMS pad is imposed to the thin film, with subsequent thermal
+		  annealing, the columns align perpendicular to the film plane. (e)
+		  Photo-cross-linking of the aligned film creates a mechanically stable thin film
+		  with vertically aligned nanopores}~\label{fig:soft} \end{figure}
+
+  Our current understanding of LLC systems is not rich enough to be able to
+  precisely design membranes for specific separations. Over the past 20 years,
+  H\textsubscript{II} phase LLC membrane studies have been limited primarily to
+  Na-GA3C11 with some characterization done after minor structural modifications.
+  Resel et al. varied the length of the monomer tails and the counterion used and
+  observed its affect on pore spacing \cite{resel_structural_2000}.  Their study
+  offers no insight into dynamics within the pore. Rejection studies show that
+  membranes formed by NA-GA3C11 can not perform separations of solutes less than
+  1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
+  We do not yet understand how to controllably reduce the effective pore size or
   how to tune the chemical environment in the nanopores for effective water
-    desalination or small organic molecule separations.
-    \item It will be challenging to efficiently narrow down the large design space in 
-    a laboratory setting without a robust model.
-    \item The only source of predictive modeling for LLC systems have been macroscopic models 
-    which likely do not adequately describe transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
-%MRS2: not quite sure of the phrasing here on next two points. Something more a long the lines of the choice of head group 
-%may allow tuning rejection of solutes based on size?
-%BJC: okay tried again
-    \item The choice of head group may allow us to tune pore size for size exclusion driven separations
-%MRS3: choice of counterion also affects size.  Counterion type probably doesn't affect Donnan potential that much IRCC, more the total amount of counterion.
-    \item Choice of counterion may influence the establishment of a Donnan potential
-    affecting the degree to which the membrane can exclude charged species.
-    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
-    structure which will be crucial to understanding the role of monomer structure in 
-    membrane design.
-    \item Molecular dynamics simulations will provide the required level of detail
-  \end{itemize}
-
-  %BJC: Figure here showing previous level of detail compared to atomistic level of detail
-  %MRS2: provenance of the atomistic figure could be explained better in the caption. It also looks disordered. Will eventually need a higher resolution figure for the previous understanding pore.
-  %BJC: Okay. The picture here is of the "ordered pore" phase. It looks disorderd from this angle. I could use a different slice of the membrane to see if it looks any better
-%MRS: if this is ordered, OK.  Maybe could try to rotate it a bit more towards the reader.
+  desalination or small organic molecule separations. The only source of
+  predictive modeling for LLC systems have been macroscopic models which likely
+  do not adequately describe transport at these length scales.
+  \cite{hatakeyama_water_2011} It will be challenging to efficiently narrow down
+  the large design space in a laboratory setting without a robust model.
+
+  A molecular level understanding of LLC membrane structure, enabled by
+  molecular dynamics simulations, will provide guidelines to reduce the large
+  chemical space available to design monomers for creation of separation-specific
+  membranes. A good molecular model should incorporate a detailed picture of the
+  nanoscopic pore structure which will be crucial to understanding the role of
+  monomer structure in solute transport and membrane design. Models resulting
+  from molecular dynamics simulations will provide the required level of detail.
+  We can directly observe solute transport and suggest governing mechanisms. We
+  can observe how the choice of head group may influence pore size for size
+  exclusion driven separations. We can interchange counterions which may
+  influence both the pore size and the strength of the Donnan potential which
+  affects the degree to which the membrane can exclude charged species.
+
+  % BJC: improve this figure
   \begin{figure}
@@
 
-  Our approach to constructing a general model will follow the development of a
-  model of a specific LLC membrane with sufficient experimental characterization.
-    \begin{itemize}
-	    \item We have chosen to focus on assemblies formed by Na-GA3C11
-	    \item We have also narrowed our scope to the development of 
-	    a model of the Col\textsubscript{h} phase membrane.
-	    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-	    phase is a simpler starting point, due to the absence of water, and has
-	    detailed experimental WAXS patterns useful for reconstructing structural data.  
-    \end{itemize}
-
-  Despite having structural data, there is still information which
-  experiment cannot definitively answer. There are several key
-  questions that we intend to answer 
-%MRS3: we can't ``answer'' for sure, since it's a model, and may omit things.
-Could put ``several key questions we will investigate'' or ``hope to provide evidence for or against'', or something like that.
-which will be laid out and numbered
-  in subsequent paragraphs.
-
-%BJC: the following just seems like filler now that I've reorganized
-%   A clear picture of the nanoscopic LLC membrane structure, gained by building 
-%   a molecular model will provide evidence to answer existing and newly proposed
-%   questions.
-%     \begin{itemize}
-%     \item Despite having structural data, there is still information which 
-%     experiment cannot definitively answer
-%     \end{itemize}
-
-%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
-%BJC: I moved the logic for choice of monomer to system to model to a separate paragraph (above this).
-I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).
-%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems.
-That is the main rationale, and it should be made clear fairly early in the introduction.
-Very important to make your story absolutely as clear as possible.
-%BJC: I moved and edited a paragraph that was originally later on to be 2 above this one.
-I think it does a better job addressing points 2 and 3.
-And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)
-
-%BJC: How question (1) and (2) used to be ordered:
-%
-%  (1) Do monomers partition into and persist as defined monomer layers?
-%  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
-%  thought to be composed of monomer layers stacked on top of each other. 
-%  \begin{itemize}
-%  	\item Their existence is supported by experimental evidence of strong 
-%	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
-%	membrane plane.
-%	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
-%	leaves no description of what is happening in monomer tail region
-%	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
-%	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
-%  \end{itemize}
-%
-%  (2) If layers do exist, how many monomers constitute a single layer?
-%  There has been no definitive answer to the question in literature.
-%  \begin{itemize}
-%    \item A simple molecular simulation study of a similar molecule suggested
-%    that there are 4 monomers in each layer. Their estimation is based on a
-%    simulated system containing only 16 total monomers which likely does not sufficiently
-%    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
-%    \item A separate calculation based on the volume of the liquid crystal monomers proposes
-%    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-%    \item A molecular model orders of magnitude larger than any other reported atomistic 
-%    liquid crystal membrane simulations has the best chance of directly answering this question.
-%  \end{itemize}
+  %BJC: I think the first sentence of the following paragraph is
+  %necessary to put somewhere, but maybe not in this spot exactly
+  In order to appropriately model transport, we must gain a thorough
+  understanding of the nanoscopic structure of LLC membranes.  Our approach to
+  constructing a general model will follow the development of a model of the
+  assembly formed by Na-GA3C11 since it has sufficient experimental
+  characterization. We have also narrowed our scope to the development of a model
+  of the Col\textsubscript{h} phase membrane. Compared to the H\textsubscript{II}
+  phase, the Col\textsubscript{h} phase is a simpler starting point, due to the
+  absence of water, and has detailed experimental Wide-angle X-ray scattering
+  (WAXS) patterns useful for reconstructing structural data.
+
+  Despite having structural data, there is still information which experiment
+  cannot definitively answer. There are several key questions that we will
+  investigate which will be laid out and numbered in subsequent paragraphs.
+
+  %BJC: commenting out :There has been no definitive answer in literature
+  %regarding the number of monomers in each layer.  MRS3: the intro to the list
+  %talks about only ``numbers of monomers in each layer'', whereas the list
+  %below talks about several questions relating to layers. Can you rephrase so
+  %it's more general? Maybe just take out that sentence above.
 
   Monomers in the Col\textsubscript{h} system are theorized to be partitioned
-  into stacked layers which form columnar pores. There has been no definitive
-  answer in literature regarding the number of monomers in each layer. 
-%MRS3: the intro to the list talks about only ``numbers of monomers in each layer'', whereas the list below talks about several questions relating to layers.
-Can you rephrase so it's more general?
-Maybe just take out that sentence above.
-We want to
-  know 
+  into stacked layers which form columnar pores. We want to know
+
   \begin{enumerate}
+
   \item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}
-  \begin{itemize}
-    \item A simple molecular simulation study of a similar molecule suggested
-    that there are 4 monomers in each layer. Their estimation is based on a
-    simulated system containing only 16 total monomers which likely does not sufficiently
-    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
-    \item A separate calculation based on the volume of the liquid crystal monomers proposes
-    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-    \item A molecular model orders of magnitude larger than any other reported atomistic 
-    liquid crystal membrane simulations has the best chance of directly answering this question.
-    \item We can directly change the layer composition and note its effect on membrane structure.
-  \end{itemize}
-
- \item Does our model support the existence of layers and if so, how well defined
-  are the layers? \label{point:layers}
-  \begin{itemize}
-       \item Experimentally, their existence is supported by evidence of strong 
-       $\pi$-$\pi$ stacking interactions in the direction perpendicular to the
-       membrane plane.
-       \item $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups which
-       leaves no description of what is happening in the monomer tail region
-       \item The tails may entangle isotropically while stacking order is maintained
-       among headgroups. 
-  \end{itemize}
-
-   \item How do monomers in each layer position themselves with respect to surrounding 
-   layers? \label{point:orientation}
-%     Even if we knew the number of monomers in each layer, we still would not know how 
-%     monomers in each layer are positioned with respect to other layers. 
-   \begin{itemize}
-      \item The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly 
-      in this system\cite{gazit_possible_2002} %is thought to be $\pi$-$\pi$ stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
-      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
-      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
-      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
-      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
-      attraction which favors the parallel displaced configuration in all cases
-      except where the substitutions are extremely electron withdrawing
-      \cite{waller_hybrid_2006,ringer_effect_2006}.
-      \item We can use simulated X-ray diffration patterns to compare the two 
-      stacking configurations. 
-   \end{itemize}
+
+  A simple molecular simulation study of a similar molecule suggested that
+  there are 4 monomers in each layer. Their estimation is based on a simulated
+  system containing only 16 total monomers which likely does not sufficiently
+  model the chemical environment present in the real system.
+  \cite{zhu_methacrylated_2006}.  A separate calculation based on the volume of
+  the liquid crystal monomers proposes that there are seven monomers in each
+  layer \cite{resel_structural_2000}.  A molecular model orders of magnitude
+  larger than any other reported atomistic liquid crystal membrane simulations
+  has the best chance of directly answering this question.  We will directly
+  change the layer composition and note its effect on membrane structure.
+
+ \item Does our model support the existence of layers and if so, how well
+ defined are the layers? \label{point:layers}
+
+  Experimentally, their existence is supported by evidence of strong $\pi$-$\pi$
+  stacking interactions in the direction perpendicular to the membrane plane.
+  $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups
+  which leaves no description of what is happening in the monomer tail region.
+  The tails may entangle isotropically while stacking order is maintained among
+  headgroups.
+
+  \item How do monomers in each layer position themselves with respect to
+  surrounding layers? \label{point:orientation}
+
+  The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly
+  in this system. \cite{gazit_possible_2002} Gas phase ab initio studies of
+  benzene dimers have shown a clear energetic advantage for parallel displaced
+  and T-shaped $\pi$-$\pi$ stacking conformations versus a sandwiched
+  conformation ~\cite{sinnokrot_estimates_2002}. Substituted benzene rings
+  exhibit an even stronger $\pi$-$\pi$ stacking attraction which favors the
+  parallel displaced configuration in all cases except where the substitutions
+  are extremely electron withdrawing.
+  \cite{waller_hybrid_2006,ringer_effect_2006}. We can use simulated X-ray
+  diffration patterns to compare the two stacking configurations.
 
@@
   accessed during experiments? \label{point:metastable}
+
   There remains the possibility that there is more than one metastable state
-  associated with a given LLC system.
-  \begin{itemize}
-    \item Simulating a membrane atomistically will require many atoms which further
-    limits the timescales acessible with MD
-    \item It is reasonable to expect that we will generate configurations which 
-    are kinetically trapped in a metastable free energy basin
-    \item We must be able to identify which state is produced experimentally and 
-    why others are not.
-  \end{itemize}
+  associated with a given LLC system. Simulating a membrane atomistically will
+  require many atoms which limits the timescales acessible with MD. It is
+  reasonable to expect that we will generate configurations which are kinetically
+  trapped in a metastable free energy basin. We must be able to identify which
+  state is produced experimentally and why others are not.
 
   \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
-  \begin{itemize}
-	\item The limited picture that experiment provides tells us that there are
-        hexagonally packed, hydrophilic regions where transport is likely to occur
-	\item One may instinctively assume that these regions are tube-like pathways
-	\item We will explore the composition of the pores and the partition
-	between the hydrophilic and hydrophobic regions. 
-  \end{itemize}
-
-  \item Is it necessary to include any water in order to appropriately model the 
-  Col\textsubscript{h} phase? \label{point:water}
-  \begin{itemize}
-	\item While the Col\textsubscript{h} phase is described as dry, it is 
-          %MRS3: ``possible'' -> likely, and give some explanations why we think likely?
-	possible that small amounts of ambient water may be leached into the system.
-	\item The hydrogen bonding network formed by the water may play a role 
-        in structuring the pore.
-	\item We can use simulated X-ray diffraction patterns to see if there is
-        any meaningful structural difference between a "dry" and "wet" system
-  \end{itemize}
+
+  The limited picture that experiment provides tells us that there are
+  hexagonally packed, hydrophilic regions where transport is likely to occur.
+  One may instinctively assume that these regions are tube-like pathways. We will
+  explore the composition of the pores and the partition between the
+  hydrophilic and hydrophobic regions.
+
+  \item Is it necessary to include any water in order to appropriately model
+  the Col\textsubscript{h} phase? \label{point:water}
+
+  While the Col\textsubscript{h} phase is described as dry, it is 
+  %MRS3: ``possible'' -> likely, and give some explanations why we think
+  %likely? 
+  likely that small amounts of ambient water may be leached into the system. The
+  hydrogen bonding network formed by the water may play a role in structuring the
+  pore.  We can use simulated X-ray diffraction patterns to see if there is any
+  meaningful structural difference between a "dry" and "wet" system
+
   \end{enumerate}
@@
    \item A third system with an initial layer spacing of 10 \angstrom was briefly
-    explored and the reader can learn more about it in the Supplemental Information.
+    explored
+   \item When layers are spaced out sufficiently, they tend to collapse on each other 
+   while simultaneously slipping in between layers of other pores which lead to an
+   artificially thick membrane with pores spaced closely together.
+   \item The intereseted reader can learn more about it in the Supplemental Information.
 % BJC: Move all this lower down to be with the rest of the equilibrium calculations
@@
         %MRS3: then just state what you did, so it could be repeated. 
-          \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-          configurations while allowing monomer tails to settle.
+          \item Restraints with a force constant of 1e6 KJ mol$^-1$ nm$^-2$, fix monomer 
+	  head groups in the sandwiched or parallel-displaced configurations while 
+          allowing monomer tails to settle.
           \item Doing so also mitigates system dependence on initial monomer configuration.
@@
           \item Every 50 ps, we reduce the force constants by the square root of its
-          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
+          previous value %, starting from 1e6 KJ mol$^-1$ nm$^-2$. <-- stated in first bullet
           \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
@@
 	%BJC: what do you mean by dynamic range?
+	%BJC: Explain how colorbar is adjusted
   \end{figure}
@@
 %MRS: not clear why some are angles with x axis, and some are angles w neighbors?  Shouldn't it be the same thing plotted in both graphs?
+%BJC: I just need to get the labels right, they are the same thing technically
   \end{figure}

### 2017-12-06 Ben_Manuscripts/structure_paper/Outline.tex
Turning outline into draft - intro text nearly done

@@
   experiment cannot definitively answer. There are several key
-  questions that we intend to answer 
+  questions that we will investigate  
 %MRS3: we can't ``answer'' for sure, since it's a model, and may omit things.
@@
   Monomers in the Col\textsubscript{h} system are theorized to be partitioned
-  into stacked layers which form columnar pores. There has been no definitive
-  answer in literature regarding the number of monomers in each layer. 
+  into stacked layers which form columnar pores. 
+%BJC: commenting out :There has been no definitive answer in literature regarding the number of monomers in each layer. 
 %MRS3: the intro to the list talks about only ``numbers of monomers in each layer'', whereas the list below talks about several questions relating to layers.
@@
 Maybe just take out that sentence above.
-We want to
-  know 
+We want to know 
 \begin{enumerate}
@@
           %MRS3: ``possible'' -> likely, and give some explanations why we think likely? 
-	possible that small amounts of ambient water may be leached into the system.
+	likely that small amounts of ambient water may be leached into the system.
 	\item The hydrogen bonding network formed by the water may play a role 

### 2017-12-07 Ben_Manuscripts/structure_paper/Draft.tex
More edits

@@
 
-  While the Col\textsubscript{h} phase is described as dry, it is 
-  %MRS3: ``possible'' -> likely, and give some explanations why we think
-  %likely? 
-  likely that small amounts of ambient water may be leached into the system. The
-  hydrogen bonding network formed by the water may play a role in structuring the
-  pore.  We can use simulated X-ray diffraction patterns to see if there is any
-  meaningful structural difference between a "dry" and "wet" system
+  While the Col\textsubscript{h} phase is described as dry, it is has been
+  suggested by experimentalists in unpublished communications that it is likely
+  that small amounts of ambient water are leached into neat monomer.
+  Experimentally, achieving a hexagonal phase with a completely dry system has
+  proven difficult. If neat monomer is allowed to sit in ambient conditions, its
+  color turns from transparent to slightly opaque and a hexagonal phase forms.
+  Although we will not explore whether water is necessary for self assembly, we
+  hypothesize that the hydrogen bonding network formed by the water may play a
+  role in structuring the pores and holding together the hexagonal phase. We can
+  use simulated X-ray diffraction patterns to see if there is any meaningful
+  structural difference between a "dry" and "wet" system.
 
@@
 
-  In this study, we build a significantly more realistic atomistic model of LLC membranes
-  than has ever previously been done, and explore what new structural information can be gained
-  and what structure hypotheses are supported by this model.
-
-  \begin{itemize}
-    \item We validate the model using as much experimental information as possible.
-    \item We are most interested in reproducing the conclusions about structure
-    which have been made from X-ray diffraction (XRD) experiments and in matching ionic
-    conductivity measurements~\cite{feng_thin_2016}.
-  \end{itemize}
-
-  We used experimental wide angle X-ray scattering (WAXS) data (produced as described
-  in~\cite{feng_scalable_2014}) and small angle X-ray scattering (SAXS) data from~\cite{feng_thin_2016}
-  to inform our choices of some initial structural parameters (Figure~\ref{fig:SWAXS}). We rely primarily
-  on the 2D WAXS data since it encodes all structural details down to the sub-nm scale.
-  \begin{itemize}
-        \item There are five major features of interest present in the 2D experimental
-        pattern shown in Figure~\ref{fig:WAXS}.
-        \item The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
-        corresponding to a real spacing of 3.7 \angstrom~. The reflection is
-        attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-        perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
-        reflection will be referred to as R-$\pi$.
-        \item A weak intensity line is located at exactly half the $q_z$ value of
-        R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a
-        real space periodic spacing of 7.4 \angstrom~. This reflection has been
-        interpreted  as 2\textsubscript{1} helical ordering of aromatic rings
-        along the z axis meaning if the positions of the aromatic rings can
-        be traced by a helix, then for each turn in the helix, there should be
-        two aromatic rings. For this reason it will be referred to as R-helix.
-        \item A third major reflection is marked by a low intensity ring located
-        at r = 1.4 \angstrom$^-1$. The real space separation
-        corresponds to 4.5 \angstrom~ which is characteristic of the average
-        spacing between packed alkane chains. This reflection will be called R-alkanes.
-        \item Within R-alkanes, are four spots of higher relative intensity which
-        will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
-        in their respective quadrants. In many liquid crystal systems this can be
-        explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: References
-        \item The final feature corresponds to the spacing and symmetry of
-        the d\textsubscript{100} plane which can be related to the distance between
-        pores. The feature, which will be called R-pores, is characterized by dots
-        along $q_z$ = 0. The spacing between dots is indicative of the hexagonal
-        symmetry of the packed pores. The same information at higher resolution is obtained using a SAXS
-        setup. By radially integrating the 2D data one gets a 1D curve which is
-        shown in Figure~\ref{fig:SAXS}.  % BJC: I also have 2D SAXS data
-  \end{itemize}
+  In this study, we build a significantly more realistic atomistic model of LLC
+  membranes than, to our knowledge, has ever previously been done, and explore
+  what new structural information can be gained and what structure hypotheses are
+  supported by this model. We validate the model using as much experimental
+  information as possible. We are most interested in reproducing the conclusions
+  about structure which have been drawn from X-ray diffraction (XRD) experiments
+  and in matching ionic conductivity measurements \cite{feng_thin_2016}.
+
+  %BJC: Would it be better to describe each reflection as a numbered list (like with the questions above?)
+  We used experimental wide angle X-ray scattering (WAXS) data (produced as 
+  described in \cite{feng_scalable_2014}) and small-angle X-ray scattering (SAXS)
+  data from \cite{feng_thin_2016} to inform our choices of some initial
+  structural parameters (Figure~\ref{fig:SWAXS}). We rely primarily on the 2D
+  WAXS data since it encodes all structural details down to the sub-nm scale.
+  There are five major features of interest present in the 2D experimental
+  pattern shown in Figure \ref{fig:WAXS}. The first is located at $q_z$ = 1.7
+  \angstrom$^{-1}$, corresponding to a real space separation of 3.7 \angstrom~.
+  The reflection is attributed to $\pi$-$\pi$ stacking between aromatic rings in
+  the direction perpendicular to the membrane plane, or z-axis
+  \cite{feng_scalable_2014}. For simplicity, this reflection will be referred to
+  as R-$\pi$. A weak intensity line is located at exactly half the $q_z$ value of
+  R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a real space periodic
+  spacing of 7.4 \angstrom~. This reflection has been interpreted as
+  2\textsubscript{1} helical ordering of aromatic rings along the z axis meaning
+  if the positions of the aromatic rings can be traced by a helix, then for each
+  turn in the helix, there should be two aromatic rings. For this reason it will
+  be referred to as R-helix. A third major reflection is marked by a low
+  intensity ring located at r = 1.4 \angstrom$^-1$. The real space separation
+  corresponds to 4.5 \angstrom~ which is characteristic of the average spacing
+  between packed alkane chains. This reflection will be called R-alkanes. Within
+  R-alkanes, are four spots of higher relative intensity which will be called
+  R-spots. All are located $\approx 40$ degrees from the $q_z$ axis in their
+  respective quadrants. In many liquid crystal systems this can be explained by
+  the tilt angle of the alkane chains with respect to the xy plane.  The final
+  feature corresponds to the spacing and symmetry of the d\textsubscript{100}
+  plane which can be related to the distance between pores.  The feature, which
+  will be called R-pores, is characterized by dots along $q_z$ = 0. The spacing
+  between dots is indicative of the hexagonal symmetry of the packed pores. The
+  same information at higher resolution is obtained using a SAXS setup. By
+  radially integrating the 2D data one gets a 1D curve which is shown in
+  Figure~\ref{fig:SAXS}.
 
@@
   \end{figure}
-
-%    \begin{itemize}
-%            \item We have compared simulated X-ray diffraction patterns to experiment in
-%            order to match major features present in the 2D patterns.
-%            \item We calculated ionic conductivity using two agreeing methods.
-%            \item We examined the the influence of crosslinking on membrane structure.
-%    \end{itemize}
-%    \item The structure-building approach and analysis used in this paper can be readily extended
-%    to the H\textsubscript{II} phase, other similar LC systems and ultimately to help design
-%    real membranes.
-%  \end{itemize}
 

### 2017-12-08 Ben_Manuscripts/structure_paper/Draft.tex
updates

@@
   osmosis since it can efficiently remove a significant portion of dissolved
-  solutes. Following NF pretreatment, RO can further purify the permeate at lower
-  pressure. Unfortunately, NF membranes, like RO, possess a pore size
+  solutes. Following NF pretreatment, RO can further purify the permeate. 
+  Unfortunately, NF membranes, like RO, possess a pore size
   distribution which limits their ability to perform precise separations
@@
   \cite{smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}
-  Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h} phase.
-  The presence of ca. 10 wt \% water results in the H\textsubscript{II} phase. In
-  both cases, monomers assemble into mesophases made of hexagonally packed,
-  uniform size, cylinders with hydrophilic head groups oriented inward towards
-  the cylinder center.  The hydrophilic region can act as a pore for aqueous
-  separations.  One can envision tailoring the pore region for specific
-  separations by changing the monomer chemsitry.
+  Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
+  phase \ref{fig:assembly} The presence of ca. 10 wt \% water results in the
+  H\textsubscript{II} phase. In both cases, monomers assemble into mesophases
+  made of hexagonally packed, uniform size, cylinders with hydrophilic head
+  groups oriented inward towards the cylinder center.  The hydrophilic region can
+  act as a pore for aqueous separations.  One can envision tailoring the pore
+  region for specific separations by changing the monomer chemsitry.
 
@@
   %permission to reprint it.
-  \begin{figure} \centering
-  \includegraphics[width=\linewidth]{soft_confinement.png} \caption{The wedge
-	  shaped liquid crystal monomer (a) self assembles into mesophases with
-		  hexagonally packed pores (b). The pores are made of stacked monomer disks. A
-		  sub-micron-thick film is created by casting a dilute solution of Na-GA3C11/THF
-		  solution onto a silicon substrate and and allowing the solvent to evaporate.
-		  The thin film contains nanoporous columns which lie parallel to the film plane.
-		  (d) When a soft PDMS pad is imposed to the thin film, with subsequent thermal
-		  annealing, the columns align perpendicular to the film plane. (e)
-		  Photo-cross-linking of the aligned film creates a mechanically stable thin film
-		  with vertically aligned nanopores}~\label{fig:soft} \end{figure}
+  %\begin{figure} \centering
+  %\includegraphics[width=\linewidth]{soft_confinement.png} \caption{The wedge
+  %	  shaped liquid crystal monomer (a) self assembles into mesophases with
+%		  hexagonally packed pores (b). The pores are made of stacked monomer disks. A
+%		  sub-micron-thick film is created by casting a dilute solution of Na-GA3C11/THF
+%		  solution onto a silicon substrate and and allowing the solvent to evaporate.
+%		  The thin film contains nanoporous columns which lie parallel to the film plane.
+%		  (d) When a soft PDMS pad is imposed to the thin film, with subsequent thermal
+%		  annealing, the columns align perpendicular to the film plane. (e)
+%		  Photo-cross-linking of the aligned film creates a mechanically stable thin film
+%		  with vertically aligned nanopores}~\label{fig:soft} \end{figure}
+
+  %BJC: Made my own version of the above, leaving out alignment details since it'
+
+  \begin{figure}
+	\centering
+	\begin{subfigure}{.3\textwidth}
+		\centering
+		%\includegraphics[width=\linewidth, trim={2.5cm 0 4cm 1.25cm}, clip]{WAXS_raw.png}
+		\includegraphics[width=\textwidth]{NaGA3C11.png}
+		\caption{}~\label{fig:monomer}
+	\end{subfigure}
+	\begin{subfigure}{.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{monomer_twocolor.png}
+		\caption{}~\label{fig:atomistic_monomer}
+	\end{subfigure}
+	\begin{subfigure}{0.3\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{wedge.png}
+		\caption{}~\label{fig:wedge}
+	\end{subfigure}
+		\begin{subfigure}{0.4\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{layer_blender.png}
+		\caption{}~\label{fig:wedge_layer}
+	\end{subfigure}
+	\begin{subfigure}{0.4\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{hexagonal_packing.png}
+		\caption{}~\label{fig:hex_packing_simple}
+	\end{subfigure}
+	\caption{The liquid crystal monomer Na-GA3C11 (a) rendered atomistically (b)
+	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
+	hydrophilic head groups (blue) facing towards the disk center. The disks
+	assemble into hexagonally packed columnnar mesophases (e)}~\label{fig:assembly}
+  \end{figure}
 
@@
 
-  %BJC: The Methods sections has four main topics which will be separated by an appropriate header
-
-  %%%%%%%%% Monomer Preparation %%%%%%%%%%%%%
-
-  Liquid crystal monomers were parameterized using the Generalized AMBER Forcefield
-  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
-  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
-  assigned using the am1bccsym method of molcharge shipped with QUACPAC from Openeye % cite with webpage
-  Scientific Software. All molecular dynamics simulations were run using Gromacs 2016  % This the version on Bridges
+  \subsection*{Monomer Placement}
+
+  Liquid crystal monomers were parameterized using the Generalized AMBER
+  Forcefield \cite{wang_development_2004} with the Antechamber package
+  \cite{wang_automatic_2006} provided with AmberTools16
+  \cite{case_ambertools16_2016}. Atomic charges were assigned using the am1bccsym
+  method of molcharge shipped with QUACPAC from Openeye Scientific Software. All
+  molecular dynamics simulations were run using Gromacs 2016.
   \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
@@
   An ensemble of characteristic, low-energy vacuum monomer configurations
-  were constructed by applying a simulated annealing process to a
-  parameterized monomer.
-  \begin{itemize}
-    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
-    \item A low energy configuration was randomly pulled from the trajectory
-    and charges were reassigned with molcharge. 
-    \item Using the new charges, the monomer system was annealed again and monomer
-    configurations were pulled from the trajectory to be used for full
-    system construction (Figure~\ref{fig:python}a).
-  \end{itemize}
-
-  %%%%%%%% UnitCell Preparation %%%%%%%%%%%%%
+  were constructed by applying a simulated annealing process to a parameterized
+  monomer. Monomers were cooled from 1000K to 50K over 10 nanoseconds.  A low
+  energy configuration was randomly pulled from the trajectory and charges were
+  reassigned using molcharge.  Using the new charges, the monomer system was
+  annealed again and a random monomer configuration was pulled from the
+  trajectory to be used for full system construction (Figure~\ref{fig:python}a).
+
+  \subsection*{Unit Cell Preparation}
 
@@
   unknown and likely outside of a reasonable length for an atomistic
-  simulation, calling for a more efficient way to build the system. 
-  \begin{itemize}
-    \item Previous work has shown a coarse grain model self assemble into
-    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
-    \item We attempted atomistic self-assembly by packing monomers into a box 
-    using Packmol \cite{martinez_packmol:_2009}.
-    \item Simulations of greater than 100 ns show no indicators of progress 
-    towards an ordered system.  %BJC: include more details in supplment
-    \item To bypass the slow self-assembly process, python scripts are used
-    to assemble monomers into a structure close to one of a number of 
+  simulation, calling for a more efficient way to build the system.  Previous
+  work has shown a coarse grain model self assemble into the H\textsubscript{II}
+  phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.  We
+  attempted atomistic self-assembly by packing monomers into a box using Packmol
+  \cite{martinez_packmol:_2009}.  Simulations of greater than 100 ns show no
+  indicators of progress towards an ordered system (See supplemental information
+  for further details). To bypass the slow self-assembly process, python scripts
+  are used to assemble monomers into a structure close to one of a number of
   hypothesized equilibrium configurations (Figure~\ref{fig:python}).
-  \end{itemize}
 
@@
   the smallest unit cell that maintains hexagonal symmetry when extended
-  periodically.
-  \begin{itemize}
-    \item Each pore is made of twenty stacked monomer layers with periodic 
+  periodically. Each pore is made of twenty stacked monomer layers with periodic
   continuity in the z direction, avoiding any edge effects and creating an
-    infinite length pore ideal for studying transport.
-%    \item Each layer is made of a set number of monomers per layer, a variable to
-%    be explored further.
-    \item A small number of layers is preferred in order to reduce computational
-    cost and to allow us to look at longer timescales.
-    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
-    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
-    This point will be explained in more detail later.
-    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information
-    %BJC: so refer to supporting info here?
-Then put plots of diffraction data with different sized system there.
-I did not explain the resolution point here because I haven't talked about simulated X-ray diffraction yet and it wouldn't make sense.
-And it doesn't make sense to talk about XRD this early in the methods but I need to justify the number of layers.
-    %MRS2: I was referring to the data choice of 20 vs 10.  Yes, you can refer to it here, because the expectation is that peple will only look at it after reading the whole paper.
-%    \item We chose initial guesses for the remaining structural parameters based on
-%    experimental data and treated them as variables during model development.
-  \end{itemize}
-
-%  We chose an initial layer spacing based on experimental 2D WAXS data.
-%  \begin{itemize}  
-%    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
-%    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
-%    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
-%    \item Our simulations tend to equilibrate to a wider interlayer spacing of
-%    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
-%    spacings greater than 4 \angstrom~.
-%  \end{itemize}
-
-  %%%%%%%%%%%% Monomer Placement %%%%%%%%%%%%%%
+  infinite length pore ideal for studying transport. A small number of layers is
+  preferred in order to reduce computational cost and to allow us to look at
+  longer timescales. Ultimately, we chose to build a system with 20 monomer
+  layers in each pore in order to obtain sufficient resolution when simulating
+  X-ray diffraction patterns. This point will be explained in more detail later.
+
+\subsection*{Monomer Placement}
 
@@
   which require careful consideration while placing monomers. The equilibrium
-  configuration is sensitive to some while insensitive to others.
-  \begin{itemize}
-	\item The starting pore radius, defined as the distance of a chosen 
-        head group carbon from the pore's central axis, does not influence the
-        equilibrium structure when a reasonable value is chosen (See Supplemental)
-        \item The pore radius is chosen to be 0.6 nm in our initial configurations 
-        because the pore size is estimated to be $\approx$ 1.2 nm % Add reference
-	\item The initial distance between pores also has little effect on the 
-        the equilibrated structure. However, one should not start them too close or there 
-        will likely be unintended high energy repulsions during early equilibration
-	\item We chose an initial pore spacing of 4.5 nm, $\approx$ 10 \% larger than 
-        the experimental value of 4.12 nm.
-        \item The distance between layers and the rotation of the layers with respect
-        to adjacent layers, and the number of monomers per layer do influence the 
-        equilibrium structure and require further justification for their choices. 
-        \item We rely on experimental data to inform our choices
-  \end{itemize}
-
-  We chose the layer spacing for the initial configuration based on R-$\pi$ 
-  and then allowed system to readjust during equilibration.
-  \begin{itemize}  
-    \item Each monomer was rotated so the plane of the aromatic head groups would
-    be coplanar with the xy plane.
-    \item We explore two different initial layer spacings
-    \item The first is exactly equal to R-$\pi$ with layers placed so aromatic
-    rings are stacked 3.7 \angstrom~ apart in the z-direction.
-    \item A second system is explored with an initial layer spacing of 5 \angstrom
-%MRS3: at least state in the main body what went wrong with it in a sentence or so, with details in supplemental. 
-   \item A third system with an initial layer spacing of 10 \angstrom was briefly
-    explored
-   \item When layers are spaced out sufficiently, they tend to collapse on each other 
-   while simultaneously slipping in between layers of other pores which lead to an
-   artificially thick membrane with pores spaced closely together.
-   \item The intereseted reader can learn more about it in the Supplemental Information.
-% BJC: Move all this lower down to be with the rest of the equilibrium calculations
-%    \item To quantify the degree of layering in our system, we calculated
-%    a spatial correlation function, $g(z)$, measured along the z-axis 
-%    (perpendicular to the membrane plane)
-%    \item To calculate $g(z)$, we binned the z component distances between 
-%    the center of mass of each benzene ring and all others of the same pore 
-%    over 50 ns of equilibrated trajectory and then normalized by the average
-%    number density.
-%    \item We compare the degree of layering between systems based on the
-%    amplitude of the first peak in $g(z)$. We halve the difference between the
-%    maximum of the first peak and the following minimum. We compare the difference
-%    to the mean to get a percentage deviation from the average number density.
-%    \item To extract the average distance between layers we applied a discrete 
-%    fourier transform to $g(z)$ and extracted the highest intensity frequency 
-  \end{itemize}
-
-% BJC: removing this since I say earlier that the system is insensitive to this choice
-% Detail will be provided in the supplement
-% discussion of measuring equilibrium pore spacing is moved down to calculations part of methods
-%  We placed pores at a chosen initial spacing based on R-pores, then allowed
-%  the system to settle into its preferred spacing. 
-%  \begin{itemize}
-    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere.
-    %BJC: Sure, but different choices of pore spacing were based on number of monomers per layer. More monomers per layer means a larger initial pore spacing.
-%    \item The model's pore centers are spaced 4.5 nm apart initially, $\approx$ 10 \% larger
-%    than the experimental value of 4.12 nm in order to reduce unintended repulsions 
-%    resulting from a tightly packed initial configuration.
-%    \item To calculate the equilibrated pore spacing, we measured the distance between pore
-%    centers.
-%    \item Pore centers were located by averaging the coordinates of sodium ions in their 
-%    respective pores.
-%    \item Statistics were generated using the bootstrapping technique (See Supplemental Information)
-    	% Supplemental vvvv
-%	\begin{itemize}
-        %MRS2: make clear sampling what?
-%        \item We are interested in 5 pore-to-pore distances which should all be equal in
-%        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
-%	\item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
-%	the system is equilibrated, we calculate how long it takes for the data in each of the 5
-%	trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
-%	\item We break the full trajectories down into sub-trajectories based on the
-%	maximum autocorrelation time of those found in the previous step. 
-%    	\item For each bootstrap trial, we recreate an equilibrium trajectory by randomly 
-%    	sampling pore spacings from the sub-trajectories 
-%    	\item We get an average value for each pore spacing by finding the mean of the bootstrapped data
-%	\item We calculate the overall average as the mean of all bootstrapped pore spacings
-%	\item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
-%	average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
-%	\item We report the mean of these uncertainties
-        % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
-	% BJC: Updated
-        % Supplemental ^^^^
-%	\end{itemize}
-%  \end{itemize}
-
-% BJC: This can be covered more in the Supplmental ... it might not even be necessary. I won't
-% report any "pore sizes" except in the supplemental where I will show that the initial choice
-% of pore radius has little effect on pore size
-
-%  We used experimental Transmission electron microscopy (TEM) and size exclusion rejection
-%  data \cite{feng_scalable_2014,feng_thin_2016,zhou_supported_2005} to inform our definition
-%  of pore radius in the initial configuration.
-%  \begin{itemize}
-%    \item Experimental evidence suggests uniform pores with radii of 0.6 nm 
-%    \item Comparing a geometric measurement of pore size derived from an atomistic model,
-%    to a less precise, experimentally derived pore size estimate, will give ambiguous results.
-%    \item What is meant by pore radius will not be clear until we establish a clear picture
-%    of the nanoscopic pore environment.
-%    \item When constructing pores, we chose the carboxylate carbon from the monomer
-%    head group as a reference atom, and placed it a distance r from the pore center,
-%    where r is the pore radius (~\ref{fig:pore_radius_illustration}). % BJC: Figure in Supplemental Information?
-%    \item We will not make direct comparisons of pore radius between our model 
-%    and experiment to avoid the ambiguity, however, we do define a pore radius  
-%    for our own purposes.
-    %\item To measure the pore radius in our model we calculate the distance between 
-    %the center of mass of each aromatic ring and the center of mass of all aromatic rings
-    %in their respective pores.
-%  \end{itemize}
-
-%MRS2: is the pore radius of the initial configuration really relevant? Does it need to be defined?  Seems like what radius means in the final equilibrated one is more important.
-%BJC: This can go in supplemental
-%  \begin{figure}
-% 	\centering
-% 	\includegraphics[width=\textwidth]{pore_radius_illustration.png}
-%	\caption{The pore radius of the initial configuration is defined using the 
-%        carboxylate carbon as a reference}~\label{fig:pore_radius_illustration}
-%  \end{figure}
+  configuration is sensitive to some while insensitive to others. The starting
+  pore radius, defined as the distance of a chosen head group carbon from the
+  pore's central axis, does not influence the equilibrium structure when a
+  reasonable value is chosen (See Supplemental). The pore radius is chosen to be
+  0.6 nm in our initial configurations because the pore size is estimated to be
+  $\approx$ 1.2 nm. The initial distance between pores also has little effect on
+  the the equilibrated structure. However, one should not start them too close or
+  there will likely be unintended high energy repulsions during early
+  equilibration. We chose an initial pore spacing of 4.5 nm, $\approx$ 10 \%
+  larger than the experimental value of 4.12 nm.  The distance between layers,
+  the rotation of the layers with respect to adjacent layers, and the number of
+  monomers per layer do influence the equilibrium structure and require further
+  justification for their choices. We rely on experimental data to inform our
+  choices
+
+  We chose the layer spacing for the initial configuration based on R-$\pi$ and
+  then allowed system to readjust during equilibration. Each monomer was rotated
+  so the plane of the aromatic head groups would be coplanar with the xy plane.
+  We explore two different initial layer spacings. The first is exactly equal to
+  R-$\pi$ with layers placed so aromatic rings are stacked 3.7 \angstrom~ apart
+  in the z-direction.  A second system is explored with an initial layer spacing
+  of 5 \angstrom. A third system with an initial layer spacing of 10 \angstrom was
+  briefly explored. When layers are spaced out too far, they will collapse
+  on each other while simultaneously slipping in between layers of adjacent pores
+  which leads to an artificially thick membrane with pores spaced closely
+  together. There will be no further discussion of this system but the interested
+  reader can learn more about it in the supplemental information.
 
   The relative interlayer orientation was chosen based on clues from
-  diffraction data as well as the various known stacking modes of benzene 
-  and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
+  diffraction data as well as the various known stacking modes of benzene and
+  substituted benzene rings: sandwiched, parallel-displaced and T-shaped
   ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
-  \begin{itemize}
-    \item The T-shaped configuration was ruled out based on the inconsistency of
-    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.
-    \item The system's preference towards the sandwiched vs. parallel displaced 
-    stacking modes will be explored.
-    \item Both have reported stacking distances near the R-$\pi$ value of 3.7 \angstrom % Reference
-    \item Headgroups in our sandwiched initial configuration are stacked directly
-    on top of each other while stacked headgroups in the parallel displaced 
-    initial configuration are offset by $180/nmon$ degrees where $nmon$ equals
-    the number of monomers per layer.
-    %BJC: I think the following commentary belongs elsewhere, maybe even in the discussion
-    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
-    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.
-This is what we fix, this is what we leave as a variable.
-The analysis probably belongs later.
-    %BJC: Yeah, I will leave the rest for discussion
-%     \item Visualization of each configuration (\Cref{fig:sandwichedlayers,fig:offsetlayers})
-%     suggests entropic differences based on the way the tails are able to pack.
-%     \item In the sandwiched configuration, all tails start out directly on top
-%     of each other which may prevent closely stacked benzene rings.
-%     \item In the offset configuration, the tails are placed in between each other 
-%     which may allow layers to come together in a compact way.
-%     \item This difference may explain, in part, which stacking mode is more favorable.
-  \end{itemize}
-
-  As outlined in \ref{point:monomernum} the number of monomers in each layer is unknown
-  so we tested configurations constructed with a varied number of monomers per layer.
-  \begin{itemize}
-	\item Systems were built in the offset and parallel displaced configurations
-        with 4, 5, 6, 7 and 8 monomers per layer
-  \end{itemize}
-
-  %%%%%%%%%%%% Equilibration %%%%%%%%%%%%%%
-
-  We developed equilibration schemes to create dry and wet configurations. Both schemes 
-  start with an initial configuration generated according to the previous guidelines.
-  \begin{itemize}
-      \item Dry equilibration scheme:
-      \begin{itemize}
-        %MRS2: what initial force constant, and does it matter (that can be in supplemental) 
-	%BJC: I've never explored whether there is any dependence on initial force constant. It probably doesn't matter unless it starts really low
-        %MRS3: then just state what you did, so it could be repeated. 
-          \item Restraints with a force constant of 1e6 KJ mol$^-1$ nm$^-2$, fix monomer 
-	  head groups in the sandwiched or parallel-displaced configurations while 
-          allowing monomer tails to settle.
-          \item Doing so also mitigates system dependence on initial monomer configuration.
-          \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
-          \item Every 50 ps, we reduce the force constants by the square root of its
-          previous value %, starting from 1e6 KJ mol$^-1$ nm$^-2$. <-- stated in first bullet
-          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
-          released linearly until there is no more restraining potential.
-          \item The resulting unrestrained structure is allowed to equilibrate for 5 ns 
-	  in the NPT ensemble with pressure controlled by the berendsen barostat.
-	  \item Long, NPT equilibration simulations are run for at least 400 ns using the 
-          Parrinello-Rahman barostat with a time consant of 10 ps.
-      \end{itemize}
-      \item Wet equilibration scheme: 
-      \begin{itemize}
-	  % BJC: the following three bullet points ended up not being the case since I used significantly less water
-          %\item We obtained an estimate of equilibrium pore water content by solvating
-          % an initial configuration with water baths above and below the membrane. 
-	  %\item We ran the solvated system according to Scheme A but with a 1000 ns equilibration
-          %\item Using that number we added water to the pores of an initial 
-	  %configuration and equilibrated according to scheme B. 
-	  \item In order to create a wet system, we solvated an initial configuration with water using gmx solvate
-          \item All water molecules placed outside the pore region are removed 
-	  \item Waters inside the pore region are randomly removed until the desired concentration
-	  of water in the pores is reached. 
-	  \item The remainder of the equilibration is the same as the dry system
-      \end{itemize}
-      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1 % BJC: supplemental
-  \end{itemize}
-
-%  An equilibration scheme with position restraints placed on aromatic rings
-  %MRS: 
-  %prevents 
-%  during early equilibration steps is required to prevent high energy repulsions .
-  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
-  %BJC: 'high energy repulsions' ?
-%  \begin{itemize}
-%    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
-%    configurations while allowing monomer tails to settle.
-%    \item Doing so also mitigates system dependence on initial monomer configuration.
-%    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
-%    \item Every 50 ps, we reduce the force constants by the square root of its 
-%    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
-%    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
-%    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
-%    restraining potential.  
-%    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
-%    ensemble for 400 - 500 ns.
-   %BJC: I will reference an equilibration script that can be released with the supplemental info
-   %MRS: we should release as many scripts as is feasible, can be in a github repository.
-   %BJC: Okay, once we submit, I will need to spend some time cleaning the scripts
-   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
-   %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
-%  \end{itemize}
-
-  %BJC: the following paragraph will be replaced with something that Joe writes
-  %MRS: sounds good.
-
-  % BJC: The following methodology is taken from the 2014 Feng et al. paper where
-  % WAXS is reported. The data we are using comes from the 2016 paper which 
-  % I assume used the same set up but I will need to verify this with Xunda
-  % before this gets sent out. The SAXS is the same as shown in the 2016 paper
-  % however I will likely reproduce it with matplotlib
-
-  %Experimental wide angle X-ray scattering measurements were performed using a 
-  %Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
-  %($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
-  %calibrations of the resultant 2-D WAXS patterns were done by using a 
-  %silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
-  %patterns were integrated into 1-D plots of scattering intensity (I) versus
-  %q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
-  %2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.
-
-%%%%%%%%%%%%% Crosslinking %%%%%%%%%%%%
-
-  Using an equilibrated structure, a crosslinking procedure was performed
-  in order to match synthetic procedures.
-  \begin{itemize}
-    \item The purpose of crosslinking is to maintain macroscopic alignment of
-    the crystalline domains, ensuring aligned, hexagonally packed pores.
-    \item For that reason, we are not concerned with replicating the kinetics
-    of the reaction, but instead emphasize the consistency of the final structure
-    with experimental structural data.
-    \item The algorithm was developed based on the known reaction mechanism.
-    \item Crosslinking of this system is a free radical polymerization (FRP)
-    taking place between terminal vinyl groups present on each of the three
-    monomer tails.
-    \item FRPs require an initiator which bonds to the system, meaning new atoms
-    were introduced into the system.
-    \item For simplicity, the initiator was simulated as hydrogen and made present
-    in the simulation by including them in all possible bonding positions as dummy atoms.
-    \item The crosslinking procedure is carried out iteratively.
-    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
-    \item The topology is updated with new bonds and dummy hydrogen atoms are
-    changed to appropriate hydrogen types.
-    \item Head-to-tail addition was the only propagation mode considered due to
-    its dominance in the real system.
-    \item Direction of attack was not considered because the resultant mixture
-    is racemic.
-    %BJC: The following items belongs in results/discussion
-    %MRS: probably. 
-    %\item The resulting crosslinked structure has an even distribution of
-    %crosslinks between monomer tails of the same monomer, monomers stacked on
-    %top of each other and monomers in other pores, including across periodic
-    %boundaries.
-    %\item The pore spacing shrinks by $\approx$ 1 \angstrom~ and stays 
-    %constant under a range of simulation conditions.
-  \end{itemize}
-
-%%%%%%%%%%%%% Equilibrium Calculations %%%%%%%%%%%%%%%
-
-  Using equilibrated structures, we carry out various calculations to characterize the
-  system. 
-  \begin{itemize}
-	\item We determine the point at which a system is equilibrated when the 
-        distance between pores stops changing
-  \end{itemize}
-
-  To calculate the equilibrated pore spacing, we measured the distance between pore
-  centers.
-  \begin{itemize}
-	\item Pore centers were located by averaging the coordinates of sodium ions in their
-	respective pores.
-	\item Statistics were generated using the bootstrapping technique (See Supplemental Information)
-	% Supplemental vvvv
-        \begin{itemize}
-        	%MRS2: make clear sampling what?
-	        \item We are interested in 5 pore-to-pore distances which should all be equal in
-	        a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
-	        \item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
-	        the system is equilibrated, we calculate how long it takes for the data in each of the 5
-	        trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
-	        \item We break the full trajectories down into sub-trajectories based on the
-	        maximum autocorrelation time of those found in the previous step.
-	        \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly
-	        sampling pore spacings from the sub-trajectories
-	        \item We get an average value for each pore spacing by finding the mean of the bootstrapped data
-	        \item We calculate the overall average as the mean of all bootstrapped pore spacings
-                  %MRS3: this sounds a little convoluted below.  Should just be the standard error in the boostrap estimates of the pore spacing?
-                  %MRS3: this can be fixed in the draft not outline.
-	        \item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
-	        average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
-	        \item We report the mean of these uncertainties
-	        % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
-	        % BJC: Updated
-        \end{itemize}
-        % Supplemental ^^^^^
-  \end{itemize}
+  The T-shaped configuration was ruled out because its $\approx$ 5 \angstrom
+  equilibrium stacking distance ~\cite{sinnokrot_estimates_2002} is inconsistent
+  with R-$\pi$. It is also unfeasible for the monomers to orient in the t-shaped
+  conformation because of the bulky tail groups. The system's preference towards
+  the sandwiched vs. parallel displaced stacking modes will be explored in some
+  detail.  Both have reported stacking distances near the R-$\pi$ value of 3.7
+  \angstrom. Headgroups in our sandwiched initial configuration are stacked
+  directly on top of each other while stacked headgroups in the parallel
+  displaced initial configuration are offset by $180/nmon$ degrees where $nmon$
+  equals the number of monomers per layer.
+
+  As outlined in \ref{point:monomernum} the number of monomers in each layer is
+  unknown. We tested configurations constructed with a varied number of
+  monomers per layer. Systems were built in the offset and parallel displaced
+  configurations with 4, 5, 6, 7 and 8 monomers per layer.
+
+  \subsection*{Equilibration}
+
+  We developed equilibration schemes to create dry and wet configurations. Both
+  schemes start with an initial configuration generated according to the previous
+  guidelines. To create a dry configuration, we fix monomer head groups in the
+  sandwiched or parallel-displaced configuration using position restraints with a
+  force constant of 1e6 KJ mol$^-1$ nm$^-2$. We run a 50 ps simulation in the
+  NVT ensemble which allows the monomer tails to settle without disrupting the
+  ordering of the head groups. Doing so also mitigates system dependence on
+  initial monomer configuration. Every 50 ps, we reduce the force constants by
+  the square root of its previous value. Once the force constant is below 10 KJ
+  mol$^-1$ nm$^-2$, the restraints are released linearly until there is no more
+  restraining potential. The resulting unrestrained structure is allowed to
+  equilibrate for 5 ns in the NPT ensemble with pressure controlled by the
+  berendsen barostat. Next, we run a long NPT equilibration simulations for at
+  least 400 ns using the Parrinello-Rahman barostat with a time consant of 10 ps.
+  In order to create a wet system, we solvated an initial configuration with
+  water using gmx solvate. All water molecules placed outside the pore region are
+  removed. Waters inside the pore region are randomly removed until the desired
+  concentration of water in the pores is reached. The remainder of the
+  equilibration follows the same procedure as the dry system. In all cases, the
+  v-rescale thermostat was used with tau-t = 0.1. % Supplemental
+
+  \subsection*{Crosslinking}
+
+  Using an equilibrated structure, we performed a crosslinking procedure
+  in order to match synthetic procedures. The purpose of crosslinking
+  is to maintain macroscopic alignment of the crystalline domains, 
+  ensuring aligned, hexagonally packed pores. For that reason, we are not
+  concerned with replicating the kinetics of the reaction, but instead emphasize
+  the consistency of the final structure with experimental structural data. The
+  algorithm was developed based on the known reaction mechanism. Crosslinking of
+  this system is a free radical polymerization (FRP) taking place between
+  terminal vinyl groups present on each of the three monomer tails. FRPs require
+  an initiator which bonds to the system, meaning new atoms are introduced into
+  the system. For simplicity, the initiator was simulated as hydrogen and made
+  present in the simulation by including them in all possible locations where an 
+  addition could occur as dummy atoms. The crosslinking procedure is carried out
+  iteratively. During each iteration, bonding carbon atoms are chosen based on
+  a distance cut-off. The topology is updated with new bonds and dummy hydrogen
+  atoms are changed to appropriate hydrogen types. Head-to-tail addition was the
+  only propagation mode considered due to its dominance in the real system.
+  Direction of attack was not considered because the resultant mixture is
+  racemic.
+
+  \subsection*{Equilibrium Calculations}
+
+  Using equilibrated structures, we carry out various calculations to
+  characterize the system. We define the point at which a system is
+  equilibrated based on when the distance between pores stops changing.
+
+  To calculate the equilibrated pore spacing, we measured the distance between
+  pore centers. Pore centers are located by averaging the coordinates of sodium
+  ions in their respective pores. Pore spacing statistics were generated 
+  using the bootstrapping technique (See Supplemental Information).
 
@@
   in our system, we calculate a spatial correlation function, $g(z)$, measured
-  along the z-axis (perpendicular to the membrane plane).
-  \begin{itemize}
-    \item To calculate $g(z)$, we binned the z component distances between
-    the center of mass of each component and all others of the same pore
-    over at least 50 ns of equilibrated trajectory and then normalized by the 
-    average number density.
-%    \item We compare the degree of layering between systems based on the
-%    amplitude of the first peak in $g(z)$. We halve the difference between the
-%    maximum of the first peak and the following minimum. We compare the difference
-%    to the mean to get a percentage deviation from the average number density.
-    \item To extract the average distance between layers we applied a discrete
-    fourier transform to $g(z)$ and extracted the highest intensity frequency
-  \end{itemize}
+  along the z-axis (perpendicular to the membrane plane). To calculate $g(z)$,
+  we binned the z-component distances between the center of mass of each
+  component and all others of the same pore over at least 50 ns of equilibrated
+  trajectory and then normalized by the average number density. To extract the
+  average distance between layers we applied a discrete fourier transform to
+  $g(z)$ and extracted the highest intensity frequency.
 
   % BJC: To be replaced by Joe's description
-  Simulated X-ray diffraction patterns were generated based on atomic
-  coordinates for a direct experimental comparison.
-  \begin{itemize}
-    \item All atomic coordinates were simulated as gaussian spheres of electron
-    density corresponding to each atom's atomic number.
-    \item A three dimensional fourier transform (FT) of the array of electron 
-    density results in a three dimensional structure factor which represents
-    the unit cell in reciprocal space.
-   % \item We perform an angular average of the structure factor about the 
-    z axis to generate a 2D cross section close to what one would see 
-    experimentally.
-    \item We matched experimental 2D WAXS patterns by adjusting the initial 
-    spacing between layers and the orientation of the head groups with respect
-    to adjacent layers.
-  \end{itemize}
+  Simulated X-ray diffraction patterns are generated based on atomic
+  coordinates in order to make a direct experimental comparison. All atomic
+  coordinates were simulated as gaussian spheres of electron density
+  corresponding to each atom's atomic number. A three dimensional fourier
+  transform (FT) of the array of electron density results in a three dimensional
+  structure factor which represents the unit cell in reciprocal space. We matched
+  experimental 2D WAXS patterns by adjusting the initial spacing between layers
+  and the orientation of the head groups with respect to adjacent layers.
 
@@
   We explored the pore composition by measuring the average number densities of
-  various monomer components with respect to the pore centers.
-  \begin{itemize}
-	\item The centers of the pores were located using the same method to
-        calculate the equilibrium pore spacing
-        \item We looked at the average number density of sodium ions, aromatic
-	rings and carbon atoms making up the monomer tails 
-	\item The radial distance from the pore center of all atoms in each group
-        are binned then normalized by area 
-	% Maybe write an equation here? It's hard to say precisely how I did it in words without it sounding confusing 
-  \end{itemize}
+  various monomer components as a function of distance from the pore centers. The
+  centers of the pores were located using the same method used to calculate the
+  equilibrium pore spacing. We looked at the average number density of sodium
+  ions, aromatic rings and carbon atoms making up the monomer tails. The radial
+  distance of all atoms in each group from the pore centers are binned, then
+  normalized by the volume of the annulus defined by the bin edges and z box
+  vector.
+  %BJC: Maybe write an equation here? It's hard to say precisely how I did it
+  %in words without it sounding confusing
 
   We calculated ionic conductivity using two different methods for robustness.
-  \begin{itemize}
-    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
-    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
-    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
-    \item Sodium ion diffusion coefficients were found by calculating the slope
-    of the linear region of the z-direction mean square displacement curve as indicated by
-    the einstein relation \cite{einstein_investigations_1956}.]
-    %MRS: state how you decided which was the linear region.
-    %BJC: nothing fancy other than looking at the msd plot and determining where to
-    % start fitting. I suppose I could minimize R^2 but that seems like overkill
-    \item We looked at the MSD plot to determine where to begin and end a linear fit
-    \item Ion concentration was measured with respect to the entire unit cell. 
-    % new paragraph
-    \item The second method, termed the 'Collective Diffusion' model, measures 
-    the movement of the collective variable, Q, which is defined as the amount
-    of charge transfer through the system and can be thought to represent
-    the center of charge of the system.
-    \item The conductance, $\gamma$ of the system can be calculated as:
-    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
-    achieved by multiplying by channel length and dividing by the membrane
-    cross sectional area.
-    \item $D_Q$ is the diffusion coefficient of the collective variable Q. It can
-    be calculated using the einstein relation.
-    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
-  \end{itemize}
+  The Nernst-Einstein relation relates the DC ionic conductivity to ion
+  diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann constant,
+  $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$. 
+  Sodium ion diffusion coefficients were found by calculating the slope
+  of the linear region of the z-direction mean square displacement curve as
+  indicated by the einstein relation \cite{einstein_investigations_1956}.] We
+  looked at the MSD plot to determine where to begin and end a linear fit. Ion
+  concentration was measured with respect to the volume of the entire unit cell.
+
+  The second method, termed the 'Collective Diffusion' model, measures the
+  movement of the collective variable, Q, which is defined as the amount of
+  charge transfer through the system and can be thought to represent the center
+  of charge of the system. The conductance, $\gamma$ of the system can be
+  calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$. Conversion to ionic
+  conductivity is achieved by multiplying by channel length and dividing by the
+  membrane cross sectional area.  $D_Q$ is the diffusion coefficient of the
+  collective variable Q. It can be calculated using the einstein relation.  A
+  full derivation of the model can be accessed elsewhere 
+  \cite{liu_collective_2013}.
 
@@
   \subsection*{Determination of Nanoscopic Structural Details}
-
-  %In order to construct an initial configuration which gives reliable 
-  %trends, we need to understand the composition of layers, how far apart
-  %to stack the layers, and how to orient them with respect to each other.
-  %\begin{itemize
-  %	\item To verify our choices for each parameter, we compare our calculations
-  %	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
-  %	scattering (WAXS), and ionic conductivity measurements.
-  %\end{itemize}
 
@@
 
-% BJC: How this section (||||) used to be ordered until deciding to put monomers / layer first
-%                        VVVV
-  %To answer (1), we verified that the system stays partitioned into layers by
-  %plotting the pair correlation function calculated between aromatic rings along
-  %the length of the pores (Fig~\ref{fig:zdf}).
-  % BJC: add how this calculation is done to methods section (put where I talk about
-  % choosing distance between layers
-  %\begin{itemize}
-%	\item Period of fluctuation (layer spacing)
- %       \item Magnitude of fluctuations
-%	\item Comment on difference between offset/layered, number of monomers per layer
- % \end{itemize}
-
-  % BJC: might replace with a figure containing alllllll of the zdf's
-  %\begin{figure}[!ht]
-%       \centering
-%       \begin{subfigure}{0.45\textwidth}
-%               \centering
-%               \includegraphics[width=\textwidth]{zdf5layered.png}
-%               \caption{}\label{fig:zdf_layered}
-%       \end{subfigure}
-%       \begin{subfigure}{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf5offset.png}
-%                \caption{}\label{fig:zdf_offset}
-%        \end{subfigure}
-%        \caption{Pair distribution functions of aromatic carbons for the
-%        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
-%        parallel displaced configurations. Clear periodic maxima in the 
-%        $z$ probability density indicate distinct layers. The magnitude 
-%        of the spikes with respect to the average suggest that the 5 
-%        monomer per layer, sandwiched configuration possesses a higher 
-%        degree of layer partitioning.}\label{fig:zdf}
-%  \end{figure}
-
-%  To discern the composition of the monomer layers, addressing \ref{point:layers}, we ran 
-%  simulations of systems created with 4 - 8 monomers per layer.
-% BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
-%MRS2: ``with between'', I'd say.
-  %\begin{itemize}
-%  	\item Both the sandwiched and parallel displaced configurations were tested.
-%	\item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
-        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
-	%BJC: Working on getting them all run out to 400 ns
-%	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
-%	\item Systems built with 5 monomers in each layer equilibrate to a pore spacing
-%	that is most consistent with the experimental value of 4.12 nm derived from
-%	SAXS measurements (Figure~\ref{fig:SAXS}).
-%	\item The remainder of this discussion will focus on the analysis of systems
-%	built with 5 monomers per layer. 
-%  \end{itemize}
-
-%MRS2: suggest starting with conclusion.
-Something like ``The simulations best support the model of 5 monomers per layer based on the pore-to-pore distances.'' Then provide evidence.
-Suggest for all points.
-
   The simulations best support a model built with 5 monomers per layer based on
   the measured pore-to-pore distances. To discern the composition of the monomer
-  layers, addressing (\ref{point:monomernum}), we ran simulations of systems created
-  with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
-  \begin{itemize}
-        \item We created systems in both the parallel displaced and sandwiched configurations
-	\item All systems were prepared according to the dry equilibration procedure
-        \item All systems are stable after 400 ns of simulation.  
-        \item Figure ~\ref{fig:p2p} shows the pore spacing for all systems tested.
-        \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
-        that is most consistent with the experimental value of 4.12 nm derived from
-        SAXS measurements (Figure~\ref{fig:SAXS}).
-        \item The remainder of this discussion will focus on the analysis of systems
-        built with 5 monomers per layer.
-  \end{itemize}
-
-  %BJC: maybe split into 2 paragraphs
-  %MRS2: usually good instinct.
-Lead with the conclusions of the research you are trying to convince readers.
-Rather than phrasing as a question.
-Something like: ``Layers are well defined and persistent''.
-  We learned that layers are well-defined and persistent, answering (\ref{point:layers})
-  %We verified that the system stays partitioned into layers by
-  We verified our conclusion by
-  plotting the pair correlation function, $g(z)$ calculated between atoms along
-  the length of the pores (Fig~\ref{fig:zdf}).
-  \begin{itemize}
-	\item We measured $g(z)$ with respect to aromatic rings in the head groups
-	and, separately, with respect to carbon atoms on the alkane chains.
-	% \item In both cases, we see a degree of layer partitioning
-        \item Using the head groups as reference, we see that sandwiched configuration
-	layers stack 4.29 \angstrom apart while parallel displaced configuration layers
-	stack 4.37 \angstrom apart.
-	\item Using the alkane chain carbons as reference we see a layer spacing of 4.39 \angstrom
-	and 4.38 \angstrom in the sandwiched and parallel displaced configurations respectively.
-        \item The power spectrums used to calculate the reported layer spacings are given in the 
-        Supplemental Information.  %BJC: "Power spectrum" an okay description here?
-	% BJC: TODO: Overlay plots of tail and headgroup densities
-        %MRS2: repore more precisely what finding is interesting. What does that difference mean?
-%	\item We see a difference in the spacing in the head group versus tail region
-%	because there is more volume to fill with less densely packed carbon chains in the tail region. 
-	% BJC: vvv Need to get the same information for the tail zdfs.
-%	\item Even though the layer spacing is similar, the sandwiched configuration
-%	exhibits more defined layers with its first peak deviating from the mean 
-%        number density by 61 \%. %BJC: I mention how I do this calculation in the methods. Is it clear that I'm doing that here?
-%MRS2: fine for description for now.          
-%	\item The parallel displaced configuration deviates from the mean by only 
-%	12 \% in comparison.
-%MRS2: is this that unexpected, since parallel displaces should have layers that alternate anyway?
-%BJC: true, but I'm just stating the facts
-  \end{itemize}
+  layers, addressing (\ref{point:monomernum}), we ran simulations of systems
+  created with 4 - 8 monomers per layer. Systems were built in both the parallel
+  displaced and sandwiched configurations and prepared according to
+  the dry equilibration procedure. All systems are stable after 400 ns of
+  simulation. Figure ~\ref{fig:p2p} shows the pore spacing for all systems
+  tested. Systems built with 5 monomers in each layer equilibrate to a pore
+  spacing that is most consistent with the experimental value of 4.12 nm derived
+  from SAXS measurements (Figure~\ref{fig:SAXS}). The remainder of this
+  discussion will focus on the analysis of systems built with 5 monomers per
+  layer.
+
+  We learned that layers are well-defined and persistent, answering
+  (\ref{point:layers}). We verified our conclusion by plotting the pair
+  correlation function, $g(z)$ calculated between atoms along the length of the
+  pores (Fig~\ref{fig:zdf}). We measured $g(z)$ with respect to aromatic rings in
+  the head groups and, separately, with respect to carbon atoms in the alkane
+  chains. We see that sandwiched configuration layers stack 4.39 \angstrom apart
+  while parallel displaced configuration layers stack 4.38 \angstrom apart.  The
+  power spectrums used to calculate the reported layer spacings are given in the
+  Supplemental Information.
+
+ \begin{figure}
+	\centering
+	\includegraphics[width=0.5\linewidth]{p2p.png}
+	\caption{The pore spacing (given in nm) of the model increases as
+	number of monomers in each layer increases. The pore spacing of a system
+	starting in the sandwiched configuration is systematically lower than 
+	that started in an offset configuration. Systems built with 5 monomers
+	per layer in a parallel displaced configuration result in a pore spacing
+	closest to the experimental 4.12 nm}~\label{fig:p2p}
+  \end{figure}
 
@@
 
-  % BJC: Even though I will shift focus to only 5 monomers per layer, I will put other data
-  % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information 
-  %MRS2: good.
-  \begin{figure}
-	\centering
-	\includegraphics[width=0.5\linewidth]{p2p.png}
-	\caption{The pore spacing (given in nm) of the model increases as
-	number of monomers in each layer increases. The pore spacing of a system
-	starting in the sandwiched configuration is systematically lower than 
-	that started in an offset configuration. Systems built with 5 monomers
-	per layer in a parallel displaced configuration result in a pore spacing
-	closest to the experimental 4.12 nm}~\label{fig:p2p}
-  \end{figure}
-
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{ccc}
-%  \toprule
-%  		   & \multicolumn{2}{c}{Starting Configuration} \\
-%  \hline
-%  Monomers per layer & Sandwiched & Parallel Displaced \\
-%  \midrule
-%  4 & $3.72 \pm 0.04$ & $3.84 \pm 0.02$ \\  % done
-%  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
-%  6 & $4.69 \pm 0.04$ & $4.72 \pm 0.03$ \\
-%  7 & $4.66 \pm 0.02$ & $4.82 \pm 0.03$ \\  % done
-%  8 & $5.00 \pm 0.04$ & $5.33 \pm 0.02$ \\
-%  \bottomrule
-%  \end{tabular}
-%  \caption{The pore spacing (given in nm) of the model increases as
-%  number of monomers in each layer increases. The pore spacing of a system
-%  starting in the sandwiched configuration is systematically lower than 
-%  that started in an offset configuration. Systems built with 5 monomers
-%  per layer in a parallel displaced configuration result in a pore spacing
-%  closest to the experimental 4.12 nm}
-%  \label{table:p2p} 
-%  \end{table}
-
-  % BJC: This paragraph needs to change since, upon inspection, it appears that the 
-  % offset configuration is correct. So it needs to shine a more positive light on offset
-  % BJC: I think it can be deleted
-  %We varied the initial relative interlayer orientation between sandwiched and 
-  %parallel-displaced based on our knowledge of the stability of the two
-  %pi-stacking modes.
-  %\begin{itemize}
-  %	\item We generated simulated X-ray diffraction patterns using simulation 
-  %      trajectories from the highly restrained initial configurations created during 
-  %	equilibration
-  %	\item The simulated patterns establish a difference between the two stacking 
-  %	modes (Figure~\ref{fig:XRDrestrained}).
-  %	\item In each pattern, R-alkanes is present at a distance of $\approx
-  %	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
-  %	\item R-$\pi$ is also present in each pattern, although it appears to 
-  %	intersect R-alkanes because the spacing between aromatic rings is 
-  %	similar to the alkane chain packing.
-  %     %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
-  %	%BJC: okay added some more specific language
-  %	\item The difference in aromatic ring spacing between experiment and
-  %	simulation is likely a result of the inability of GAFF to properly handle
-  %	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
-  %	\item The sandwiched configuration shows R-spots in the expected location.
-  %	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
-  %	\item The parallel displaced configuration contains two lines of high 
-  %	intensity with maximum intensity occurring where they intersect the alkane
-  %	chain region due to constructive interference between the two features.
-  %	\item The lines are located where one would expect to see R-helix and, 
-  %	perhaps coincidentally, the intersection with R-alkanes occurs where one 
-  %	would expect to see R-spots.
-	%BJC: might save the following sentence for equilibrium trajectories
-  %	\item As the simulation is progressed, the full line begins to fade 
-  %	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
-  %	where R-helix exists.
-  %\end{itemize}
-
-  %\begin{figure}[!ht]
-  %	\centering
-  %	\begin{subfigure}{0.475\textwidth}
-  %		\hspace{-1.2cm}
-  %		\centering
-  %		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
-  %		\caption{}\label{fig:rzplayeredrestrained}
-  %	\end{subfigure}
-  %	\begin{subfigure}{0.475\textwidth}
-  %		\hspace{-1.2cm}
-  %		\centering
-  %		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
-  %		\caption{}\label{fig:rzoffsetrestrained}
-  %	\end{subfigure}
-  %	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
-  %	with restraints placed on aromatic carbons shows all major features
-  %	present in experimental WAXS. Near solid lines at constant z are a result of 
-  %	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
-  %	restrained parallel displaced configuration may also contain all
-  %	major experimental WAXS features. One can argue that R-spots is not present
-  %	but it is difficult to distinguish because of its intersection with the solid
-  %	R-helix line. 
-        %MRS: Longer simulations are necessary to determine which structure
-	% is the best match to experiment
-        %MRS: we probably want to avoid saying this (above) if we can.
-%}\label{fig:XRDrestrained}
-%  \end{figure}
-
-  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.
-Something to think about.
-  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
-  %MRS: make sure the figures are comparable.
-Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
-
-  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  %patterns produced from equilibrated MD trajectories shows the most consistency
-  %with the offset configuration in the OP basin.
-
-% BJC: Re-written without mention of basins in follwoing paragraph
- % We answer question (3) by simulating X-ray diffraction patterns produced from
- % equilibrated MD trajectories. We leave open the possibility that the 
- % experimental structure might be reminiscent of the parallel displaced or sandwiched
- % configuration in the OP or CP basin.
-  %We created systems using three distinct initial configurations and examined
-  %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
-%  \begin{itemize}
-%  	\item OP Basin systems were built in both the parallel displaced and sandwiched 
-%	configurations with an intial layer spacing of 3.7 \angstrom~.
-%	\item A third system was created by stacking layers in the sandwiched 
-%	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
-%	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
-%	\item The three systems were equilibrated according to our procedure with
-%	NPT simulations of greater than 400 ns.
-%	\item Simulated diffration patterns were generated using portions of the
-%	trajectory after equilibration.  
-%	\item We assume the simulation has equilibrated when the distance between 
-%	pores and the membrane thickness stopped changing.
-%	\item Simulated diffraction patterns for all three structures are shown in 
-%	Figure ~\ref{fig:XRDsim}. 
-%  \end{itemize}
-
-  We answer question (\ref{point:orientation}) by simulating X-ray diffraction patterns produced from
-  equilibrated MD trajectories.
-  %We created systems using three distinct initial configurations and examined
-  %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
-  \begin{itemize}
-	\item Systems of 5 monomers per layer in the parallel displaced and sandwiched
-	configurations were tested.
-        \item Simulated patterns were generated using portions of simulation
-        trajectory after equilibration.
-        \item The patterns for both structures are shown and compared to experiment
-	in Figure ~\ref{fig:XRDsim}.
-  \end{itemize}
-%
-
-  %BJC: below (commented out) thesis is from when I had the following three paragraphs combined
-  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
-  %patterns shows the most consistency with the offset configuration in the OP basin.
-
-%  Simulated diffraction of the disordered pore structure in the both the sandwiched
-%  and parallel displaced configurations does not match the experimental pattern.
-%  \begin{itemize}
-%        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
-%	R-$\pi$ and R-spots are not present. 
-%        \item Due to low resolution, making out the individual spots of R-pores is
-%        challenging and can be validated with slightly better resolution upon full
-%        spherical integration of the 3D structure factor. However, the same
-%        information can be extracted by measuring the pore spacing as described earlier.
-%        %BJC: ^^^This can be more concise 
-%        \item Although the structure's diffraction pattern is very different from
-%        experiment, its long-term stability suggests that the structure is realistic.
-%	We will explore this further when addressing (4). 
-%  \end{itemize}
-
-  %BJC: Put this paragraph first since it is the conclusion I want to stick
+  We answer question (\ref{point:orientation}) by simulating X-ray diffraction
+  patterns produced from equilibrated MD trajectories. We tested systems built
+  with 5 monomers per layer in the parallel displaced and sandwiched
+  configurations.  Simulated patterns were generated using portions of simulation
+  trajectory after equilibration. The patterns for both structures are shown and
+  compared to experiment in Figure ~\ref{fig:XRDsim}.
+
+  Simulated XRD of the sandwiched configuration contains all experimental
+  features except for R-helix. R-alkanes, R-spots and R-pores appear in the
+  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
+  a q value lower than experiment meaning the rings prefer to stack further
+  apart.
+
   The parallel displaced configuration results in a simulated XRD pattern with
-  the closest match to experiment.
-  \begin{itemize}
-        \item It produces the only pattern that exhibits all major reflections
-        \item R-alkanes, R-pores and R-$\pi$ appear as they do in the sandwiched configuration.
-        \item R-spots appears, however with a lower intensity relative to R-alkanes
-        when compared to the sandwiched configuration.
-        \item R-helix appears apparently due to the parallel displaced aromatic rings
-        %BJC: Maybe a figure to explain why this happens
-  \end{itemize}
-
-  %BJC: Put this paragraph second so people understand why it is wrong and don't fixate on how nice the spots are
-  Simulated XRD of the sandwiched configuration contains all experimental features
-  except for R-helix.
-  \begin{itemize}
-        \item R-alkanes and R-pores appear in the expected locations.
-        \item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
-        in experiment. The rings prefer to stack $\approx 4.2 \angstrom$ apart as % update distance if needed
-        opposed to 3.7 \angstrom~.
-        \item Most notably, R-spots appears in the expected location, which suggests 
-        that there is something intrinsic to closer packing that gives rise 
-        to such features. 
-  \end{itemize}
-
-% BJC: Replacement figure below this one
-%  \begin{figure}[!ht]
-%	\centering
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
-%		\caption{}\label{fig:sandwich_rzplot}
-%	\end{subfigure}
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{offset_rzplot.png}
-%		\caption{}\label{fig:offsetrzplot}
-%	\end{subfigure}
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\hspace{-0.9cm}
-%		\includegraphics[width=\textwidth]{disorder_rzplot.png}
-%		\caption{}\label{fig:disorder_rzplot.png}
-%	\end{subfigure}
-%	\caption{(a) All major features except R-helix are present in
-%	XRD patterns resulting from an equilibrated sandwiched configuration 
-%	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
-%	(b) All major features execpt R-spots are present in XRD patterns 
-%	resulting from an equilibrated parallel displaced configuration in Basin A.
-%	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
-%	are the only major features present in XRD patterns resulting from an 
-%	equilibrated disordered phase}\label{fig:XRDsim}
- % \end{figure}
-
-%  \begin{figure}[ht]
-%  \begin{subfigure}{.83\linewidth}
-%        \centering
-%        \begin{subfigure}{0.4\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth, trim={2.5cm 0 4cm 2cm}, clip]{WAXS_raw.png}%
-%                \caption{}~\label{fig:raw_waxs}
-%        \end{subfigure}%
-%        \begin{subfigure}{0.4\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_offset.png}
-%                \caption{}~\label{fig:rz_offset}
-%        \end{subfigure}
-%        \begin{subfigure}{0.4\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_layered.png}
-%                \caption{}~\label{fig:rz_layered}
-%        \end{subfigure}%
-%        \begin{subfigure}{0.4\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth, trim={2cm 0 2.5cm 1.25cm}, clip]{rzplot_disordered.png}
-%                \caption{}~\label{fig:rz_disordered}
-%        \end{subfigure}
-%  \end{subfigure}%
-%  \begin{subfigure}{0.14\linewidth}
-%        \centering
-%        \vspace{-1cm}
-%        \includegraphics[width=\linewidth]{colorbar_jet.png}
-%  \end{subfigure}
-%  \caption{(a) Experimental 2D WAXS data contains 5 major reflections which we aim to match. The remaining
-%  three images are diffraction patterns simulated from MD trajectories. (b) The parallel displaced
-%  configuration gives rise to all reflections of interest. (c) The sandwiched configurations gives rise to a
-%  pattern with all major reflections except R-helix. R-spots is strong relative to R-alkanes in comparison
-%  to the parallel displaced configuration. (d) The disordered pore configuration creates a pattern with only
-%  R-alkanes and R-pores in common with experiment}~\label{fig:xrd}
-%  \end{figure}
+  the closest match to experiment. It produces the only pattern that exhibits
+  all major reflections. R-alkanes, R-pores and R-$\pi$ appear as they do in the
+  sandwiched configuration. R-spots appears, however with a lower intensity
+  relative to R-alkanes when compared to the sandwiched configuration. R-helix
+  appears apparently due to the parallel displaced aromatic rings
 
@@
 
-  R-spots, which appears in both simulated XRD patterns, is a result of the way 
-  alkane tails pack together.
-  \begin{itemize}
-  	\item Previously, the spots in the diffraction pattern had been explained 
-	as the product of tilted alkane chains. % BJC: reference 2014 ACS nano paper
-	\item We measured the tilt angle of the alkane chains and showed that our 
-	system equilibrates to an average tilt angle close to zero degrees ~\ref{fig:tilt} % Could belong in supplemental. Leaving here for now 
-	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
-	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
-        that the spots arise as a consequence of the tails. 
-	\item By removing atoms from the trajectory and simulating a diffraction 
-	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails}).
-	\item Since the tails stay nearly flat, we plotted the centroids of the 
-	tails and measured the angle between each centroid and its nearest neighbors
-	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).  %BJC: at one point Matt mention doing a correlation function instead of just measuring the angles
-	\item We see distinct peaks in the distribution of these angles (Figure~\ref{fig:tail_packing})
-  \end{itemize}
+  R-spots, which appears in both simulated XRD patterns, is a result of
+  hexagonal alkane chain packing. Previously, the spots in the diffraction
+  pattern had been explained as the product of tilted alkane chains. We measured
+  the tilt angle of the alkane chains and showed that our system equilibrates to
+  an average tilt angle close to zero degrees ~\ref{fig:tilt}. To understand the
+  origin of the spots, we determined which atoms gave rise to the feature. Since
+  R-spots is present as higher intensity spots within R-alkanes, it is likely
+  that the spots arise as a consequence of the tails. By removing atoms from the
+  trajectory and simulating a diffraction pattern, we were able to isolate the
+  cause of the spots to the tails (Figure~\ref{fig:tails}).  Since the tails stay
+  nearly flat, we plotted the centroids of the tails and measured the angle
+  between each centroid and its nearest neighbors with respect to the plane of
+  the membrane (Figure~\ref{fig:centroids}).  %BJC: at one point Matt mention
+  doing a correlation function instead of just measuring the angles We see
+  distinct peaks in the distribution of these angles 
+  (Figure~\ref{fig:tail_packing}).
 

### 2017-12-08 Ben_Manuscripts/structure_paper/supplemental.tex
updates

@@
 \maketitle
+
+n{itemize}
+                %MRS2: make clear sampling what?
+                \item We are interested in 5 pore-to-pore distances which should all be equal in
+                a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
+                \item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
+                the system is equilibrated, we calculate how long it takes for the data in each of the 5
+                trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
+                \item We break the full trajectories down into sub-trajectories based on the
+                maximum autocorrelation time of those found in the previous step.
+                \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly
+                sampling pore spacings from the sub-trajectories
+                \item We get an average value for each pore spacing by finding the mean of the bootstrapped data
+                \item We calculate the overall average as the mean of all bootstrapped pore spacings
+                  %MRS3: this sounds a little convoluted below.  Should just be the standard error in the boostrap estimates of the pore spacing?
+                  %MRS3: this can be fixed in the draft not outline.
+                \item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
+                average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
+                \item We report the mean of these uncertainties
+                % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
+                % BJC: Updated
+        \end{itemize}
 

### 2017-12-08 Ben_Manuscripts/structure_paper/Draft.tex
updates

@@
   The $z$-direction correlation functions show that layers in our model prefer
-  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration
-  with layers stacked 5.0 nm apart and to our surprise, we observed
-  long-term stability of a qualitatively different configuration suggesting
-  that we have found more than one metastable free energy basin, corroborating \ref{point:metastable}.
-  %that the initial distance between layers can influence the approach towards 
-  %equilibrium.
+  to stack further apart than 3.7 \angstrom as suggested by experiment. We
+  attempted equilibration with layers stacked 5.0 nm apart and to our surprise,
+  we observed long-term stability of a qualitatively different configuration
+  suggesting that we have found more than one metastable free energy basin,
+  corroborating \ref{point:metastable}.
   \begin{itemize}
-        \item Equilibrated systems built according to the 3.7 \angstrom~layer spacing
-        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore
-        structure.
-        \item We will refer to this large set of configurations, with an open pore, as
-        the ordered pore basin open pore (Figure~\ref{fig:OPbasin}).
-        \item Simulations of systems built with layers stacked 5
-        \angstrom~ apart results in a pore structure characterized by high radial
-        disorder, while still maintaining partitioning between hydrophobic and
-        hydrophilic regions.
- %MRS3: need to address the similar RDFs.
-What data can show they are different?
-Or maybe they HAVE rdfs, but not good layering?
-Have you done the fourier transform on them?
-We can still rule them out based on the XRD, of course.
-But surprising the same RDFs.
-        \item This will be called the disordered pore basin (Figure~\ref{fig:DPbasin}).
-        \item This LLC membrane may exist in at least two metastable states.
-        \item The distinct difference in pore structure exhibited by each phase will
-        likely lead to different transport mechanisms.
-        \item Because the pore structure will vary between each basin, understanding
-        which phase exists experimentally is necessary in order to ensure we are
-        studying the system which actually dominates.
+ 	\item The diffraction pattern is different in the tail region
+	\item The layer spacing is further apart
   \end{itemize}
@@
 
-  % BJC: I'm not sure what to make of this figure right now. The parallel-displaced configuration shares
-  % more with the disordered pore phase
-  % MRS3: yeah, see my notes on this.  wE need to understand how it can be visually open, and still have this structure.  
-  % doesn't this structur have a different pore-to-pore distance.
   \begin{figure}
@@
   \end{figure}
-
-%MRS3: this needs a caption, and need to write some text analyzing it.
-The thing that throws me off is that the RDF's look about the same for parallel displaced and disordered!
-That's pretty hard to rationalize with the idea that the pores are open vs.
-closed.
-What am I missing?
-Very interesting regardless!
 

### 2017-12-12 Ben_Manuscripts/structure_paper/Draft.tex
Filling out text & some new figures

@@
   The simulations best support a model built with 5 monomers per layer based on
-  the measured pore-to-pore distances. To discern the composition of the monomer
-  layers, addressing (\ref{point:monomernum}), we ran simulations of systems
-  created with 4 - 8 monomers per layer. Systems were built in both the parallel
-  displaced and sandwiched configurations and prepared according to
-  the dry equilibration procedure. All systems are stable after 400 ns of
-  simulation. Figure ~\ref{fig:p2p} shows the pore spacing for all systems
-  tested. Systems built with 5 monomers in each layer equilibrate to a pore
-  spacing that is most consistent with the experimental value of 4.12 nm derived
-  from SAXS measurements (Figure~\ref{fig:SAXS}). The remainder of this
-  discussion will focus on the analysis of systems built with 5 monomers per
-  layer.
+  the measured pore-to-pore distances. To discern the composition of the
+  monomer layers, addressing (\ref{point:monomernum}), we ran simulations of
+  systems created with 4 - 8 monomers per layer. Systems were built in both the
+  parallel displaced and sandwiched configurations and prepared according to the
+  dry equilibration procedure. All systems are stable after 400 ns of simulation.
+  In a sense, all systems are at least metastable, addressing
+  \ref{point:metastable}, however not all will make physical sense or fit the
+  experimental profile that we are looking to match. Figure ~\ref{fig:p2p}
+  shows the pore spacing for all systems tested. Systems built with 5 monomers in
+  each layer equilibrate to a pore spacing that is most consistent with the
+  experimental value of 4.12 nm derived from SAXS measurements
+  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the
+  analysis of systems built with 5 monomers per layer.
 
@@
 
-  The peaks in the tilt angle distribution are consistent with the location of R-spots.
-  \begin{itemize}
-	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
-	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
-	of spots are located on the simulated patterns
-	\item We confirmed this conclusion by radially integrating the 2D WAXS pattern for q values
-	between 1.57 and 1.4 (real space between 4 and 4.5 \AA) 
-	\item We observe that distinct peaks appear c.a. 30 $\degree$, in close agreement with the
-	previously measured angle distribution (~\ref{fig:offset_integration}~\ref{fig:layered_integration})
-%	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
-	\item We performed the same integration on the raw experimental data and found the angle
-	at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a 
+  The peaks in the tilt angle distribution are consistent with the location of
+  R-spots. The peaks of interest in Figures \ref{fig:offset_tails} and
+  \ref{fig:layered_tails} are located at $\pm$ 33 $\degree$ which is the same
+  location where the highest intensity of spots are located on the simulated
+  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
+  pattern for q values between 1.57 and 1.4 (real space between 4 and 4.5 \AA). We
+  observe that distinct peaks appear ca. 30 $\degree$, in close agreement with
+  the previously measured angle distribution
+  (~\ref{fig:offset_integration}~\ref{fig:layered_integration}). We performed the
+  same integration on the raw experimental data and found the angle at which
+  R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a
   reconcilable difference with our simulated results.
-  \end{itemize}
 
@@
   (b) and (d) respectively.}~\label{fig:tail_packing}
-%MRS2: not clear what the difference is between right and left side figures.
-%BJC: That's good! One is angles measured between tail centroids and the other is radial integration of the simulated xrd patterns. I'll try make that more clear in the caption.
-%MRS3: sorry, I meant to say not clear what the SOURCE of the data is in right vs. left.  Make sure colors and labels are consistent in final 
-%MRS: not clear why some are angles with x axis, and some are angles w neighbors?  Shouldn't it be the same thing plotted in both graphs?
-%BJC: I just need to get the labels right, they are the same thing technically
-  \end{figure}
-
-  The $z$-direction correlation functions show that layers in our model prefer
-  to stack further apart than 3.7 \angstrom as suggested by experiment. We
-  attempted equilibration with layers stacked 5.0 nm apart and to our surprise,
-  we observed long-term stability of a qualitatively different configuration
-  suggesting that we have found more than one metastable free energy basin,
-  corroborating \ref{point:metastable}.
+  \end{figure}
+
+%  The $z$-direction correlation functions show that layers in our model prefer
+%  to stack further apart than 3.7 \angstrom as suggested by experiment.
+  When systems are built with layers stacked 5.0 \angstrom apart then equilibrated, 
+  we observe long-term stability of a qualitatively different configuration
+  suggesting that we have found another metastable free energy basin,
+  further corroborating \ref{point:metastable}. We studied this type of system in
+  both the parallel displaced and sandwiched configurations.
+
+  Structural properties are different when layers are initially spaced 5 \AA apart.
   \begin{itemize}
- 	\item The diffraction pattern is different in the tail region
-	\item The layer spacing is further apart
+	\item In both configurations we observe a decrease in pore spacing along with an increase in the equilibrated distance between layers.
+	\item The simulated X-ray diffraction patterns differ particularly with reference to R-spots.
+	\item R-helix is still faintly visible in the parallel displaced and absent in the sandwiched simulated diffraction pattern implying that head groups maintain their initial ordering to a degree.
+	\item In both cases, R-spots is markedly different.
+	\item When layers stack too far apart, they do not exhibit hexagonal packing
+	\item The intensity within R-alkanes of the parallel displaced configuration is nearly uniform with slightly more concentrated intensity at the top and bottom.
+	\item The sandwiched configuration possesses higher intensity regions at the top and bottom of R-alkanes as well as along the equator with high intensity near q$_z$ = 0.
   \end{itemize}
 
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:OPbasin}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
-                \caption{}\label{fig:DPbasin}
-        \end{subfigure}
-        \caption{From a qualitative standpoint, the ordered pore basin (a) is characterized by a
-        hollow cylindrical pore while pores in the disorder pore basin (b) are characterized by a
-        higher degree of radial disorder}\label{fig:basins}
-%MRS3: see note on RDF.
-  \end{figure}
-
-  % INSERT XRD of disordered basin
-
-  In order to address \ref{point:poredefinition} and to further understand the structural difference 
-  between the ordered pore and disordered pore basins, we plotted the number of densities of
-  heavy atoms in the head group and tail regions of the monomers in addition to the sodium ions.
-  (See Supplemental Information for definition of head group and tail regions) 
-  \begin{itemize}
-	\item For the hydrophilic region, we used the carbon atoms making up the aromatic ring
-	\item For the hydrophobic components we used all carbon atoms of the monomer tails
-  \end{itemize}
+  \begin{figure}
+        \centering
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{offset_disordered_rzplot.png}
+                \caption{}~\label{fig:offset_disordered_xrd}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{layered_disordered_rzplot.png}
+                \caption{}~\label{fig:layered_disordered_xrd}
+        \end{subfigure}
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{dbwl.png}
+                \caption{}~\label{fig:dbwl_disordered}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{p2p2.png}
+                \caption{}~\label{fig:p2p_disordered}
+        \end{subfigure}
+	\caption{In comparison to systems built with 3.7 \AA initial layer spacing,  
+                the simulated X-ray diffraction patterns of the parrallel displaced (a) and 
+ 		sandwiched (b) configurations are different when systems are built with 
+ 		a 5 \AA initial layer spacing, most notably in the region bounded by R-alkanes.
+      		When layers are stacked further apart, the distance between layers increases (c)
+                and the pore spacing decreases (d).}
+  \end{figure}
+
+  In order to address \ref{point:poredefinition}, we plotted the number of
+  densities of heavy atoms in the head group and tail regions of the monomers in
+  addition to the sodium ions. (See Supplemental Information for definition of
+  head group and tail regions). For the head group region, we used the carbon
+  atoms making up the aromatic ring For the tail regions we used only carbon
+  atoms of the monomer tails
 
@@
 
-  We answer (\ref{point:water}) and further support (\ref{point:orientation}) by preparing parallel displaced and
-  sandwiched configurations according to the wet equilibration procedure.
-  \begin{itemize}
-	\item We do not have an experimental measurement of water in the pores
-	\item We tested a range of water concentrations from 0.5 to 5 percent % working on a 0.5 wt % sytstem now just to see
-	\item Our lower bound represents a system with on average 2 water 
-	molecules for each monomer layer.
-	\item Figure ~\ref{fig:solvation} shows results for each configuration.
-%	\item Initially, we decided the number of waters to put in each pore by
-%	estimating the number of hydrogen bonds in which pore entities could participate.
-%	\item In solution, each headgroup has a charge of -1
-%	\item We estimate there to be at least 2 water molecules per layer based 
-%	on various packing configurations and geometric constraints
-%	\item 4 water molecules per layer translates to about 1.6 wt \%
-  \end{itemize}
+  % BJC: necessary to show layered configurations at this point?
+  We answered (\ref{point:water}) and further support (\ref{point:orientation})
+  by preparing parallel displaced and sandwiched configurations according to the
+  wet equilibration procedure. There is no experimental measurement of trace
+  water concentration in the pores. We tested a range of water concentrations
+  from 0.5 to 5 percent. Our lower bound models a system with on average 2 water
+  molecules for each monomer layer. Figure ~\ref{fig:solvation} shows the
+  simulated diffraction patters resulting from each configuration.
 
@@
 
-  In all cases, water disrupts structuring of the model.
-  \begin{itemize}
-	\item The plots in Figure ~\ref{fig:solvation} are normalized 
-	to have the same colorbar as the dry systems. 
-	\item The intensity of the reflections decrease when water is 
-	added to the system.
-	\item In systems built with 5 weight percent water, R-$\pi$ and
-	R-spots become nearly indistinguishable from R-alkanes.
-  \end{itemize}
+  In all cases, water disrupts structuring of the model. The plots in Figure
+  ~\ref{fig:solvation} are normalized to have the same colorbar as the dry
+  systems. The intensity of the reflections decrease when water is added to the
+  system. In systems built with 5 weight percent water, R-$\pi$ and R-spots
+  become nearly indistinguishable from R-alkanes.
 
@@
 
-  %BJC: old version of above figure v v v
-  %\begin{figure}[ht]
-  %\centering
-
-  %\begin{subfigure}{0.3\linewidth}
-  %      \centering
-  %      \includegraphics[width=\linewidth]{offset_tail_packing.png}
-  %      \caption{}~\label{fig:offset_tails}
-  %\end{subfigure}
-  %\begin{subfigure}{0.3\linewidth}
-  %      \centering
-  %      \includegraphics[width=\linewidth]{angles_traj_layered.png}
-  %      \caption{}~\label{fig:layered_tails}
-  %\end{subfigure}
-  %\begin{subfigure}{0.3\linewidth}
-  %      \centering
-  %      \includegraphics[width=\linewidth]{integrated_WAXS_ring.png}
-  %      \caption{}~\label{fig:rz_layered}
-  %\end{subfigure}
-  %\caption{The distribution of angles w.r.t. xy plane between alkane chain tail centroids and nearest
-  %neighbor centroids for equilibrated parallel displaced (a) and sandwiched (b) configurations both show
-  %distinct peaks at $\pm$ 33 $\degree$. (c) Integrated 2D WAXS data between $q_r$=1 and $q_r$=1.42 shows
-  %distinct peaks at with maxima at $\pm$ 37 $\degree$}~\label{fig:tail_packing}
-  %\end{figure}
-
-%BJC: basin stuff that won't be included in this paper
-%  The disordered basin shares little in common with the ordered basin but 
-%  its long term stability suggests that it can exist under some conditions.  
-%  We observed that Basin B is the dominant configuration at higher temperatures.
-%  \begin{itemize}
-%        \item We linearly ramped the temperature of a system in Basin A
-%        from 280K to 340K (just below the experimental isotropic transition temperature) over 100 ns.
-%        \item Visually, there is a distinct change in pore structure from one
-%        characteristic of the OP Basin (Figure~\ref{fig:280K_pore}) to one characteristic of
-%        the CP Basin (Figure~\ref{fig:340K_pore}).
-%        \item The slope of all order parameters changes between 315K and 325K
-%        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
-%        possibility of an abrupt change in system ordering.
-%        \item Our 100 ns temperature ramp was likely too fast and caused the system
-%        to suffer from hysteresis.
-%  \end{itemize}
-
-%  We can not immediately classify the OP Basin and the CP Basin as separate phases.
-%  \begin{itemize}
-%	\item To prove the existence of two phases we need evidence of a
-%	a first order phase transition.
-%	\item A first order phase transition can be denoted by a discontinuity
-%        of some order parameter in response to an external condition such as
-%	temperature.
-%	\item We chose three easily measurable order parameters: the distance
-%	between pores, the membrane thickness and the ratio of pore radius to
-%	the uncertainty in pore radius.  % BJC: these may change
-%        \item The pore radius is divided by its uncertainty as a way of quantifying
-%        the degree to which monomers obstruct the pore region.
-%  \end{itemize}
-
-% In an attempt to mitigate hysteresis, we performed slow, stepwise temperature ramps
-%  on a parallel displaced and a sandwiched configuration previously equilibrated at 300K.
-%  \begin{itemize}
-%        \item Every 200 ns, the temperature was raised 5K until we reached 345K
-%	\item We performed the same procedure with a system equilibrated in the CP Basin
-%	and used it as a benchmark for comparison. 
-%  \end{itemize}
-%
-%  \begin{figure}[!ht]
-%        \centering
-%        \begin{subfigure}[b]{0.475\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-%                \caption{}\label{fig:280K_pore}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.475\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
-%                \caption{}\label{fig:340K_pore}
-%        \end{subfigure}
-%        \vskip\baselineskip
-%        \begin{subfigure}[b]{0.325\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{p2p_tramp.png}
-%                \caption{}\label{fig:p2p_tramp}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.325\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{thickness_tramp.png}
-%
-%                \caption{}\label{fig:thickness_tramp}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.325\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{order_tramp.png}
-%                \caption{}\label{fig:order_tramp}
-%        \end{subfigure}
-%        \caption{(a) The open pore structure exhibited by a structure equilibrated
-%        at 280K is characteristic of the OP Basin. (b) The closed pore structure with
-%        a high degree of radial disorder exhibited when the structure in (a) is
-%        heated to 340K is characteristic of the CP Basin. (c) A plot of distance between pores
-%        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
-%        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
-%        its uncertainty changes slope near 315K.}\label{fig:tramp}
-%  \end{figure}
-
-%  The CP and OP basins are two configurationally metastable basins.
-%  \begin{itemize}
-%        \item There is litle change in CP basin properties during the 
-%        temperature ramp.
-%	\item We observed smooth changes in order parameters as temperature
-%        of the OP Basin system was increased implying that we cannot claim the
-%	existence of two phases (Figure~\ref{fig:phase_transition}).
-%	\item Qualitatively, the pore structure of the OP basin system becomes
-%        comparable to one characteristic of the CP basin as temperature is raised. (\Cref{fig:BasinA_280K_pore,fig:BasinB_340K_pore})
-%	\item The OP basin system does not converge to the same order parameter
-%	values as the CP basin, however it is trending towards Basin B values. (\Cref{fig:p2p_step,fig:thickness_step,fig:order_step})
-%	\item To resolve the quanitative discrepancy, we would need a slower 
-%	temperature ramp
-%	\item Since there are no abrupt changes in any order parameter along the 
-%	trajectory, we can conclude that the two basins are not separate phases
-%	\item The OP basin is the closest match to what is seen experimentally
-%	\item The CP basin is likely an intermediate between the Col\textsubscript{h} 
-%	phase and isotropic phase
-%	\item The CP basin is present in our simulations at lower temperatures 
-%        %MRS: lower temperatures than experiment.  Though nobody has really done the experiments.  
-%        %MRS: can we conclude anything from some of the in-situ temperature measurements done by Xunda?  We talked about them, but I don't know they are referenced here.
-%	%BJC: Not with what we have because it's in-situ SAXS data which only shows the pore spacing
-%	than experiment because our model lacks sufficient $\pi$-$\pi$ iteractions necessary to 
-%	stabilize the system into the OP basin. 
-%  \end{itemize} 
-%
-%  \begin{figure}[!ht]
-%        \centering
-%	% BJC: I'll get actual pictures of the system here. I'm not sure how 
-%	% necessary this figure is though. It could go in the supplemental 
-%	% information and I can reference the pictures in the previous figure
-%	% since they show basically the same idea : Ordered vs. disordered pore
-%	% Alternatively, I could show two diffraction patterns here from the 
-%	% beginning and end temperature 
-%        \begin{subfigure}[b]{0.475\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-%                \caption{}\label{fig:BasinA_280K_pore}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.475\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
-%                \caption{}\label{fig:BasinB_340K_pore}
-%        \end{subfigure}
-%	\vskip\baselineskip
-%        \begin{subfigure}[b]{0.325\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{p2p_layered.png}
-%                \caption{}\label{fig:p2p_step}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.325\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{thickness_layered.png}
-%
-%                \caption{}\label{fig:thickness_step}
-%        \end{subfigure}
-%        \begin{subfigure}[b]{0.325\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{order_layered.png}
-%                \caption{}\label{fig:order_step}
-%        \end{subfigure}
-%
-%	\caption{In all cases, blue lines represent the measured value of
-%	the order parameter, black lines are average values calculated from
-%	equilibrated Basin B systems at each temperature, green shaded regions
-%	represent the standard deviation of each of the black line values, and 
-%	red dashed lines show where the temperature is bumped to the next level.
-%	(a) At 280K, the system is in a configuration reminiscent of
-%	Basin A. (b) At 335K, the system resembles a Basin B configuration. (c) The pore
-%	spacing of Basin A decreases with temperature approaching the value 
-%	exhibited by Basin B. (d) The thickness of Basin A increases smoothly with 
-%	temperature but is far from the Basin B value. Longer equilibrations at 
-%	each temperature are needed to allow the system to fully expand. 
-%        (e) The ratio of pore radius to uncertainty for Basin A changes smoothly with temperature,
-%	converging to a value below that exhibited by Basin B.}\label{fig:phase_transition}
-%  \end{figure}
-
   \subsection*{Ionic conductivity calculation}
@@
   We use the equilibrated parallel displaced system to calculate ionic
-  conductivity since its structure is the closest match to experiment.
-  The model gives reasonable estimates of ionic conductivity when compared to 
-  experiment.
-  \begin{itemize}
-  	\item Calculated values of ionic conductivity obtained using the Nernst 
-	Einstein relation and Collective Diffusion model are compared in 
-	Figure~\ref{fig:conductivity}.
-	\item The two methods agree with each other within error, although the 
-	uncertainty obtained using the Collective Diffusion model is much higher.
-	\item Much longer simulations are needed to lower the uncertainty, however it
-	is not feasible to do so with a large system.  
-	\item For this reason we will likely only use the Nernst Einstein relation
-	in future calculations of this type. 
-  \end{itemize}
+  conductivity since its structure is the closest match to experiment. The model
+  gives reasonable estimates of ionic conductivity when compared to experiment.
+  Calculated values of ionic conductivity obtained using the Nernst Einstein
+  relation and Collective Diffusion model are compared in
+  Figure~\ref{fig:conductivity}. The two methods agree with each other within
+  error, although the uncertainty obtained using the Collective Diffusion model
+  is much higher. Much longer simulations are needed to lower the uncertainty,
+  however it is not feasible to do so with a large system. We will only use the
+  Nernst Einstein relation in future calculations of this type.
 
   The calculated values of ionic conductivity are higher than experiment by an
-  order of magnitude. 
-  \begin{itemize}
-	\item One can justify the reason for this result by considering the 
-	real system studied experimentally
-	\item The ionic conductivity measurement to which we are comparing was done
-	on a \SI{80}{\micro\metre} thick film, nearly 10,000 times thicker than 
-        our simulated system. 
-	\item The thick film likely has defects leading to non-contiguous pores and
-	imperfect alignment.
-	\item The 2D SAXS pattern shows the small degree of tortuosity present
-	in the system (~\ref{fig:2DSAXS})  % BJC: insert 2D SAXS data -- maybe azimuthal distribution
-	\item It has been shown that there is a large dependence of Ionic conductivity
-	on the alignment of the pores
-	\item The ionic conductivity of an unaligned film is 85 times lower than that
-	of a nearly aligned film referenced here  % BJC: reproduce figure from 2014
-	\item It is not unreasonable that a thin, perfectly aligned film would have 
+  order of magnitude. One can justify the reason for this result by considering
+  the real system studied experimentally. The ionic conductivity measurement to
+  which we are comparing was done on a \SI{80}{\micro\metre} thick film, nearly
+  10,000 times thicker than our simulated system. The thick film likely has
+  defects leading to non-contiguous pores and imperfect alignment. The 2D SAXS
+  pattern shows the small degree of tortuosity present in the system
+  (~\ref{fig:2DSAXS}). It has been shown that there is a large dependence of
+  ionic conductivity on the alignment of the pores. The ionic conductivity of an
+  unaligned film is ca. 85 times lower than that of a nearly aligned film
+  referenced here. We hypothesize that a thin, perfectly aligned film would have
   a value of ionic conductivity in agreement with our model
-  \end{itemize}
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\linewidth]{2D-SAXS_cropped.png}
-  % BJC: I will add axes with q values if this ends up in the final draft
-  % BJC: I'll also see what I can do about all the white speckles
-%MRS2: I'm not sure what the point of this figure is?
-%BJC: I put it here at some point in case the need arises. It's mainly to show
-% that the pores in the real system are somewhat tortuous, in place of showing
-% the Azimuthal distribution which is just an integration of this data. I thought
-% it'd be clearer that way since but maybe it's not?
-%MRS3: state more clearly in the caption why you are showing it. i.e. ``this data shows that pores in the system are somewhat tortuous'', then explain how the figure shows that.
-  \caption{The experimental two dimensional SAXS pattern exhibits reflections
-  resulting from highly aligned pore regions. A perfectly aligned system 
-  would exhibit sharp dots at the same locations of the refelctions shown. 
-  An isotropically aligned system the reflections would appear as 
-  rings centered about the origin}~\label{fig:2DSAXS}
-  \end{figure}
 
@@
 
-%  The CP basin has a higher ionic conductivity than the OP basin.
-%  \begin{itemize}
-%	\item We hypothesize that conductivity is enhanced in Basin B due to a 
-%	higher sodium ion diffusivity.
-%	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
-%	Sodium ions have less nearby sites to move to in Basin A.
-%	\item There is currently no experimental evidence of this trend. Maybe Xunda will find something
-%	\item In both cases, our calculated values for Basin A are higher than the 
-%	experimental values, as expected. 
-%	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
-%	\item However, the real system, although mostly aligned and straight, has a 
-%	distribution of azimuthal angles, meaning that the pores have a degree of 
-%	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
-%	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
-%	fold increase in ionic conductivity. We would expect additional gains in a 
-%	perfectly aligned system.
-%  \end{itemize}
-
-%BJC: vvv replaced by bar plot above
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{ccc}
-%  \toprule
-%  \multicolumn{3}{c}{Calculated Ionic Conductivity \si{\siemens\per\meter}} \\
-%  \hline
-%  Method & Basin A & Basin B \\
-%  \midrule
-%  Nernst Einstein & \num{1.23e-4} (0.01) & \num{1.76e-4} (0.02) \\
-%  Collective Diffusion & \num{1.40e-4} (0.32) & \num{4.6e-4}(2.4) \\
-%  Experiment & \num{1.33e-5} (0.10) & -- \\
-%  \bottomrule
-%  \end{tabular}
-%  \caption{Calculated ionic conductivity using Nernst-Einsten and Collective Diffusion 
-%  agree within error. Both methods give calculated values of ionic conductivity which
-%  are an order of magnitude higher than experimental values~\label{table:conductivity}}.
-%  \end{table}
-
-  %MRS: the next sections maybe should be supporting?
-  %MRS: you say ``the distance decreases by 1 A'' but is that true
-  %over all of the different structures?
-  %BJC: limiting the discussion to the OP basin in the offset configuration 
-  %MRS: Maybe show the difference before and after crosslinking in X-ray, to show that you can't tell?
-  %MRS: you don't otherwise discuss clearly what effect crosslinking would have. 
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{2D-SAXS_cropped.png}
+  \caption{Experiments confirm that the pores have a small degree of tortuosity. 
+  The experimental two dimensional SAXS pattern exhibits reflections
+  resulting from highly aligned pore regions. A perfectly aligned system 
+  would exhibit sharp dots at the same locations of the refelctions shown. 
+  An isotropically aligned system the reflections would appear as 
+  rings centered about the origin}~\label{fig:2DSAXS}
+  \end{figure}
+
   \subsection*{Implementation of the crosslinking algorithm}
@@
 
-%  \begin{figure}
-%	\centering
-%	\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
-%		\caption{}\label{fig:p2p_diagram}
-%	\end{subfigure}
-%		\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
-%		\caption{}\label{fig:no_xlink_p2p}
-%	\end{subfigure}
-%		\begin{subfigure}{0.31\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{xlink_p2p.png}
-%		\caption{}\label{fig:xlink_p2p}
-%	\end{subfigure}
-%	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
-%	Each numbered circle represents a pore. Distances are measured along each of the 
-%	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
-%	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
-%	individual pores in the crosslinked system are stable relative to the uncrosslinked
-%	system}\label{fig:xlink}
-%  \end{figure}
-
   \section*{Conclusion}
 
-  We have used a detailed molecular model of the Col\textsubscript{h} phase formed by NA-GA3C11
-  in order to study the nanoscopic structure.
-  \begin{itemize}
-  	\item While there have been efforts to model formation of various liquid crystalline 
-	phases with molecular dynamics, to our knowledge there have been no studies which 
-	attempt to examine their structure with the same level of detail presented here.
-	\item Evidence strongly supports that layers are composed of 5 monomers
-        \item We have confirmed that monomers stay partitioned in layers.
-	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
-	membrane strucure. 
-	\item Simulated diffration patterns generated from MD trajectories suggest that
-	the parallel-displaced configuration produces a structure with the closest match to experiment.
-%MRS3: water is not needed to create well-defined pore structures?  I'm not sure ``maintain'' is the right word, and ``membrane structure'' may be too vague.
-	\item Finally, water is not needed to maintain membrane structure our data 
-	shows that it actually disorders the pore
-	\item Now that we have a good idea of what the membrane structure should look like, we will
-	evaluate transport of various solutes within the system. 
-         %MRS2: I'd like to see a bit more information about ``pore size'', and the RDF's of the constituents.  What FITS through a pore is another paper.
-        \item We will apply the knowledge gained from this study in order to 
-        suggest improvements to the existing system as well as to evaluate new
-	unsynthesized LLC systems.
-%	\item Even though our model only answers these questions for a system created by 
-%	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
-%	little extra effort. 
-  \end{itemize}
+  % add stuff about pore structure and 'disordered' basin once there are concrete results 
+  We have used a detailed molecular model of the Col\textsubscript{h} phase
+  formed by NA-GA3C11 in order to study its nanoscopic structure. While there
+  have been efforts to model formation of various liquid crystalline phases with
+  molecular dynamics, to our knowledge there have been no studies which attempt
+  to examine their structure with the same level of detail presented here.
+  Evidence strongly supports that layers are composed of 5 monomers. We have
+  confirmed that monomers stay partitioned into layers. We have explored the
+  affect of two different $\pi$-$\pi$ stacking modes on the equilibrated membrane
+  strucure. Simulated diffration patterns generated from MD trajectories suggest
+  that the parallel-displaced configuration produces a structure with the closest
+  match to experiment. Finally, water is not needed to create well-definied pore
+  structures. Now that we have a good idea of what the membrane structure should
+  look like, we will evaluate transport of various solutes within the system. We
+  will apply the knowledge gained from this study in order to suggest
+  improvements to the existing system as well as to evaluate new unsynthesized
+  LLC systems.
 

### 2017-12-15 Ben_Manuscripts/structure_paper/Draft.tex
New figures and plotting capabilities
polishing text

@@
 
-  \section*{Introduction}
+  \section{Introduction}
 
@@
   small molecules can be achieved using reverse osmosis (RO) or nanofiltration
-  (NF). \cite{van_der_bruggen_review_2003}
-
-  While RO and NF have seen many advances in the past few decades, they are far
-  from perfect separation technologies. Current commericial RO membranes are thin
-  film composite membranes with a porous support layer and an active layer made
-  of a dense polyamide polymer matrix.  The membranes are unstructured with
-  tortuous and polydisperse diffusion pathways. Separation occurs as solutes
-  dissolve into and diffuse through voids in the polymer matrix at different
-  rates.\cite{wijmans_solution-diffusion_1995} With optimization, one can exploit
-  these differences to create a functional selective barrier. High feed pressures
-  are required in order to achieve economical solvent flux. The largest
-  application of reverse osmosis is desalination. A typical seawater desalination
-  process requires feed pressures in the range of 800 to 1000 psi in order to
-  overcome osmotic pressure. \cite{fritzmann_state---art_2007} Only 0.5 \% of the
-  world's water is fresh. Desalination is an important source of potable water,
-  necessary in order to keep up with demand generated by a rapidly growing global
-  population. Although RO is currently the cheapest form of desalination, the
-  cost must be further decreased in order to meet demand. By designing better
-  membranes for desalination, we can achieve higher water fluxes and lower feed
-  pressure requirements which will decrease the cost of fresh water production.
+  (NF) \cite{van_der_bruggen_review_2003}. While RO and NF have seen many
+  advances in the past few decades, they are far from perfect separation
+  technologies.
+
+  Current commercial RO membranes are thin film composite membranes with a
+  porous support layer and an active layer made of a dense polymer matrix. The
+  membranes are unstructured with tortuous and polydisperse diffusion pathways.
+  Separation occurs based on differences in solubility and diffusivity of solutes
+  within the polymer matrix \cite{wijmans_solution-diffusion_1995}. With
+  optimization, one can exploit these differences to create a functional
+  selective barrier. RO operation costs are suboptimal because high feed
+  pressures are required in order to achieve a useful solvent flux.
+
+  %BJC : I don't know that this paragraph fits.  
+  Improved RO membranes can make desalination more sustainable. Only 0.5 \% of
+  the world's water is fresh. Desalination is an important source of potable
+  water, necessary in order to keep up with demand generated by a rapidly growing
+  global population. Although RO is currently the cheapest form of desalination,
+  the cost must be further decreased in order to meet demand. A typical seawater
+  desalination process requires feed pressures in the range of 800 to 1000 psi
+  \cite{fritzmann_state---art_2007}. By designing better membranes for
+  desalination, we can achieve higher water fluxes and reduce feed pressure
+  requirements which will decrease the cost of fresh water production.
   \cite{humplik_nanostructured_2011}.
@@
   have a surface charge resulting from ionizable groups which affords separation
-  of ions smaller than the pore readius by Donnan exclusion.
-  \cite{van_der_bruggen_review_2003} NF is often used as a precursor to reverse
+  of ions smaller than the pore radius by the mechanism of Donnan exclusion
+  \cite{van_der_bruggen_review_2003}. NF is often used as a precursor to reverse
   osmosis since it can efficiently remove a significant portion of dissolved
@@
   are atomically thick which results in excellent water permeability but defects
-  during manufacturing severely impact selectivity.
-  \cite{cohen-tanugi_multilayer_2016} Molecular dynamics simulations of carbon
+  during manufacturing severely impact selectivity
+  \cite{cohen-tanugi_multilayer_2016}. Molecular dynamics (MD) simulations of carbon
   nanotubes show promise \cite{humplik_nanostructured_2011} but synthetic
@@
   added benefits of low cost and synthetic techniques feasible for large scale
-  production.  \cite{feng_scalable_2014} LLC systems created by the monomer named
-  Na-GA3C11 have been extensively studied experimentally.
+  production.  \cite{feng_scalable_2014} LLC systems created by the monomer 
+  Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied experimentally.
   \cite{smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}
   Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-  phase \ref{fig:assembly} The presence of ca. 10 wt \% water results in the
+  phase (Fig.\ref{fig:assembly}). The presence of ca. 10 wt \% water results in the
   H\textsubscript{II} phase. In both cases, monomers assemble into mesophases
@@
   the mesophases could be aligned using a magnetic field with subsequent
-  crosslinking to lock the structure in place. \cite{feng_scalable_2014} In 2016,
+  crosslinking to lock the structure in place \cite{feng_scalable_2014}. In 2016,
   Feng et al. showed that the same result could be obtained using a technique
-  termed soft confinement. \cite{feng_thin_2016}
+  termed soft confinement \cite{feng_thin_2016}.
 
@@
   observed its affect on pore spacing \cite{resel_structural_2000}.  Their study
-  offers no insight into dynamics within the pore. Rejection studies show that
-  membranes formed by NA-GA3C11 can not perform separations of solutes less than
-  1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
-  We do not yet understand how to controllably reduce the effective pore size or
-  how to tune the chemical environment in the nanopores for effective water
-  desalination or small organic molecule separations. The only source of
-  predictive modeling for LLC systems have been macroscopic models which likely
-  do not adequately describe transport at these length scales.
-  \cite{hatakeyama_water_2011} It will be challenging to efficiently narrow down
-  the large design space in a laboratory setting without a robust model.
+  offers no insight into dynamics within the pore. In a later study of rejection
+  performance, it was shown that membranes formed by Na-GA3C11 can not perform
+  separations of solutes less than 1.2 nm in diameter because the pores are too
+  large \cite{zhou_supported_2005}.  We do not yet understand how to controllably
+  reduce the effective pore size or how to tune the chemical environment in the
+  nanopores for effective water desalination and small organic molecule
+  separations. The only source of predictive modeling for LLC systems have been
+  macroscopic models which likely do not adequately describe transport at these
+  length scales \cite{hatakeyama_water_2011}. It will be challenging to
+  efficiently narrow down the large design space in a laboratory setting without
+  a robust model.
 
@@
   %necessary to put somewhere, but maybe not in this spot exactly
-  In order to appropriately model transport, we must gain a thorough
+  In order to appropriately model transport, we must first gain a thorough
   understanding of the nanoscopic structure of LLC membranes. Our approach to
@@
   phase, the Col\textsubscript{h} phase is a simpler starting point, due to the
-  absence of water, and has detailed experimental Wide-angle X-ray scattering
+  absence of water, and has detailed experimental wide-angle X-ray scattering
   (WAXS) patterns useful for reconstructing structural data.
@@
   cannot definitively answer. There are several key questions that we will
-  investigate which will be laid out and numbered in subsequent paragraphs.
+  investigate.
+% which will be laid out and numbered in subsequent paragraphs.
 
@@
   system containing only 16 total monomers which likely does not sufficiently
-  model the chemical environment present in the real system.
+  model the chemical environment present in the real system
   \cite{zhu_methacrylated_2006}.  A separate calculation based on the volume of
@@
   The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly
-  in this system. \cite{gazit_possible_2002} Gas phase ab initio studies of
+  in this system \cite{gazit_possible_2002}. Gas phase ab initio studies of
   benzene dimers have shown a clear energetic advantage for parallel displaced
@@
   are extremely electron withdrawing.
-  \cite{waller_hybrid_2006,ringer_effect_2006}. We can use simulated X-ray
-  diffration patterns to compare the two stacking configurations.
+  \cite{waller_hybrid_2006,ringer_effect_2006}. We will compare simulated X-ray
+  diffration patterns to experiment in order to deduce which stacking 
+  configurations is most likely.
 
@@
   trapped in a metastable free energy basin. We must be able to identify which
-  state is produced experimentally and why others are not.
+  state is produced experimentally.
 
@@
 
-  While the Col\textsubscript{h} phase is described as dry, it is has been
-  suggested by experimentalists in unpublished communications that it is likely
+  While the Col\textsubscript{h} phase is described as dry, it has been
+  suggested by experimentalists, in unpublished communications, that it is likely
   that small amounts of ambient water are leached into neat monomer.
@@
 
+  %BJC: Would it be better to describe each reflection as a numbered list (like with the questions above?)
+  We used experimental small-angle X-ray scattering (SAXS) data from
+  \cite{feng_thin_2016} (Fig. ~\ref{fig:SAXS}) and wide angle X-ray scattering
+  (WAXS) data (Fig. ~\ref{fig:WAXS}, produced as described in
+  \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
+  since it encodes all structural details down to the sub-nm scale.  There are
+  five major features of interest present in the 2D experimental pattern shown in
+  Figure \ref{fig:WAXS}. The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
+  corresponding to a real space separation of 3.7 \angstrom~.  The reflection is
+  attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
+  perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For
+  simplicity, this reflection will be referred to as R-$\pi$. A weak intensity
+  line is located at exactly half the $q_z$ value of R-$\pi$ ($q_z$ = 0.85
+  \angstrom$^{-1}$), corresponding to a real space periodic spacing of 7.4
+  \angstrom~. This reflection has been interpreted as 2\textsubscript{1} helical
+  ordering of aromatic rings along the z axis meaning if the positions of the
+  aromatic rings can be traced by a helix, then for each full turn in the helix, one
+  will encounter two aromatic rings. For this reason it will be referred to as
+  R-helix. A third major reflection is marked by a low intensity ring located at
+  r = 1.4 \angstrom$^{-1}$. The real space separation corresponds to 4.5 \angstrom~
+  which is characteristic of the average spacing between packed alkane chains.
+  This reflection will be called R-alkanes. Within R-alkanes, are four spots of
+  higher relative intensity which will be called R-spots. All are located
+  $\approx 37$ degrees from the $q_z$ axis in their respective quadrants. In many
+  liquid crystal systems this can be explained by the tilt angle of the alkane
+  chains with respect to the membrane plane. The final feature corresponds to the
+  spacing and symmetry of the d\textsubscript{100} plane which can be related to
+  the distance between pores.  The feature, which will be called R-pores, is
+  characterized by dots along $q_z$ = 0. The spacing between dots is indicative
+  of the hexagonal symmetry of the packed pores. The same information at higher
+  resolution is obtained using a SAXS setup.
+
   In this study, we build a significantly more realistic atomistic model of LLC
@@
 
-  %BJC: Would it be better to describe each reflection as a numbered list (like with the questions above?)
-  We used experimental wide angle X-ray scattering (WAXS) data (produced as 
-  described in \cite{feng_scalable_2014}) and small-angle X-ray scattering (SAXS)
-  data from \cite{feng_thin_2016} to inform our choices of some initial
-  structural parameters (Figure~\ref{fig:SWAXS}). We rely primarily on the 2D
-  WAXS data since it encodes all structural details down to the sub-nm scale.
-  There are five major features of interest present in the 2D experimental
-  pattern shown in Figure \ref{fig:WAXS}. The first is located at $q_z$ = 1.7
-  \angstrom$^{-1}$, corresponding to a real space separation of 3.7 \angstrom~.
-  The reflection is attributed to $\pi$-$\pi$ stacking between aromatic rings in
-  the direction perpendicular to the membrane plane, or z-axis
-  \cite{feng_scalable_2014}. For simplicity, this reflection will be referred to
-  as R-$\pi$. A weak intensity line is located at exactly half the $q_z$ value of
-  R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a real space periodic
-  spacing of 7.4 \angstrom~. This reflection has been interpreted as
-  2\textsubscript{1} helical ordering of aromatic rings along the z axis meaning
-  if the positions of the aromatic rings can be traced by a helix, then for each
-  turn in the helix, there should be two aromatic rings. For this reason it will
-  be referred to as R-helix. A third major reflection is marked by a low
-  intensity ring located at r = 1.4 \angstrom$^-1$. The real space separation
-  corresponds to 4.5 \angstrom~ which is characteristic of the average spacing
-  between packed alkane chains. This reflection will be called R-alkanes. Within
-  R-alkanes, are four spots of higher relative intensity which will be called
-  R-spots. All are located $\approx 40$ degrees from the $q_z$ axis in their
-  respective quadrants. In many liquid crystal systems this can be explained by
-  the tilt angle of the alkane chains with respect to the xy plane.  The final
-  feature corresponds to the spacing and symmetry of the d\textsubscript{100}
-  plane which can be related to the distance between pores.  The feature, which
-  will be called R-pores, is characterized by dots along $q_z$ = 0. The spacing
-  between dots is indicative of the hexagonal symmetry of the packed pores. The
-  same information at higher resolution is obtained using a SAXS setup. By
-  radially integrating the 2D data one gets a 1D curve which is shown in
-  Figure~\ref{fig:SAXS}.
-
   \begin{figure}
@@
                 \centering
-        %       \vspace{12mm}
                 \includegraphics[width=\linewidth]{SAXS.png}
@@
                 \centering
-                \raisebox{.2\textwidth}{%
                 \includegraphics[width=\linewidth]{WAXS_annotated.png} 
-                }
                 \caption{}\label{fig:WAXS}
         \end{subfigure}
-        \caption{(a) 1D small angle X-ray scattering indicates hexagonal packing of
-        pores as well as the spacing between pores (b) 2D wide angle X-ray scattering
-        gives details about repeating features less than 1 nanometer apart}\label{fig:SWAXS}
-  \end{figure}
-
-  \section*{Methods}
-
-  \subsection*{Monomer Placement}
+	\caption{(a) The repeat spacing in the 1D small angle X-ray scattering pattern
+		is characteristic of hexagonal packing. The leading peak represents the
+		distance between the d\textsubscript{100} planes. Using this distance, we know
+		that the distance between pore centers is 4.12 nm. (b) 2D wide angle X-ray
+		scattering gives details about repeating features less than 1 nanometer
+		apart. Experimentalists have justified each of the 5 major reflections
+		present as follows: (I) Aromatic head group $\pi-\pi$ stack 3.7 \AA~apart.
+		(II) Monomers arrange vertically in a 2\textsubscript{1} helix. (III) Alkane
+ 		chain tails pack 4.5 \AA~apart. (IV) Monomer tails tilt with respect to the 
+ 		membrane plane. (V) As derived from SAXS, pores pack hexagonally and are 
+		spaced 4.12 nm apart}
+	\label{fig:SWAXS}
+ \end{figure}
+
+  \section{Methods}
+
+  \subsection{Monomer Parameterization}
 
@@
 
-  \subsection*{Unit Cell Preparation}
+  \subsection{Unit Cell Preparation}
 
   The timescale for self assembly of monomers into the hexagonal phase is
-  unknown and likely outside of a reasonable length for an atomistic
-  simulation, calling for a more efficient way to build the system.  Previous
-  work has shown a coarse grain model self assemble into the H\textsubscript{II}
-  phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.  We
+  unknown and likely outside of a reasonable length for an atomistic simulation,
+  calling for a more efficient way to build the system.  Previous work has shown
+  a coarse grain model self assemble into the H\textsubscript{II} phase
+  configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.  We
   attempted atomistic self-assembly by packing monomers into a box using Packmol
   \cite{martinez_packmol:_2009}.  Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system (See supplemental information
-  for further details). To bypass the slow self-assembly process, python scripts
-  are used to assemble monomers into a structure close to one of a number of
-  hypothesized equilibrium configurations (Figure~\ref{fig:python}).
+  indicators of progress towards an ordered system To bypass the slow
+  self-assembly process, python scripts are used to assemble monomers into a
+  structure close to one of a number of hypothesized equilibrium configurations
+  (Figure~\ref{fig:python}).
 
@@
   layers in each pore in order to obtain sufficient resolution when simulating
-  X-ray diffraction patterns. This point will be explained in more detail later.
-
-\subsection*{Monomer Placement}
+  X-ray diffraction patterns. %This point will be explained in more detail later.
+
+\subsection{Monomer Placement}
 
@@
   the the equilibrated structure. However, one should not start them too close or
-  there will likely be unintended high energy repulsions during early
-  equilibration. We chose an initial pore spacing of 4.5 nm, $\approx$ 10 \%
-  larger than the experimental value of 4.12 nm.  The distance between layers,
-  the rotation of the layers with respect to adjacent layers, and the number of
-  monomers per layer do influence the equilibrium structure and require further
-  justification for their choices. We rely on experimental data to inform our
-  choices
+  there will be high energy repulsions during early equilibration. We chose an
+  initial pore spacing of 4.5 nm, $\approx$ 10 \% larger than the experimental
+  value of 4.12 nm.  The distance between layers, the rotation of the layers with
+  respect to adjacent layers, and the number of monomers per layer do influence
+  the equilibrium structure and require further justification for their choices.
+  We rely on experimental data to inform them.
 
   We chose the layer spacing for the initial configuration based on R-$\pi$ and
-  then allowed system to readjust during equilibration. Each monomer was rotated
+  then allowed the system to readjust during equilibration. Each monomer was rotated
   so the plane of the aromatic head groups would be coplanar with the xy plane.
@@
   ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
-  The T-shaped configuration was ruled out because its $\approx$ 5 \angstrom
+  The T-shaped configuration was ruled out because its $\approx$ 5 \angstrom~
   equilibrium stacking distance ~\cite{sinnokrot_estimates_2002} is inconsistent
-  with R-$\pi$. It is also unfeasible for the monomers to orient in the t-shaped
+  with R-$\pi$. It is also unfeasible for the monomers to orient in the T-shaped
   conformation because of the bulky tail groups. The system's preference towards
@@
 
-  As outlined in \ref{point:monomernum} the number of monomers in each layer is
+  As outlined in (\ref{point:monomernum}) the number of monomers in each layer is
   unknown. We tested configurations constructed with a varied number of
@@
 
-  \subsection*{Equilibration}
+  \subsection{Equilibration}
 
@@
   sandwiched or parallel-displaced configuration using position restraints with a
-  force constant of 1e6 KJ mol$^-1$ nm$^-2$. We run a 50 ps simulation in the
+  force constant of 1e6 KJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in the
   NVT ensemble which allows the monomer tails to settle without disrupting the
@@
   the square root of its previous value. Once the force constant is below 10 KJ
-  mol$^-1$ nm$^-2$, the restraints are released linearly until there is no more
+  mol$^{-1}$ nm$^{-2}$, the restraints are released linearly until there is no more
   restraining potential. The resulting unrestrained structure is allowed to
   equilibrate for 5 ns in the NPT ensemble with pressure controlled by the
-  berendsen barostat. Next, we run a long NPT equilibration simulations for at
+  berendsen barostat. Next, we run long NPT equilibration simulations for at
   least 400 ns using the Parrinello-Rahman barostat with a time consant of 10 ps.
+
   In order to create a wet system, we solvated an initial configuration with
@@
   concentration of water in the pores is reached. The remainder of the
-  equilibration follows the same procedure as the dry system. In all cases, the
-  v-rescale thermostat was used with tau-t = 0.1. % Supplemental
-
-  \subsection*{Crosslinking}
-
-  Using an equilibrated structure, we performed a crosslinking procedure
-  in order to match synthetic procedures. The purpose of crosslinking
+  equilibration follows the same procedure as the dry system.
+
+  \subsection{Crosslinking}
+
+  % BJC: Need to make it clear that this was not done on all systems
+
+  In order to fully match synthetic procedures, we created a crosslinking
+  algorithm that can be applied to equilibrated structures. The purpose of 
+  crosslinking
   is to maintain macroscopic alignment of the crystalline domains, 
@@
 
-  \subsection*{Equilibrium Calculations}
+  Our implementation requires long simulation times to achieve high degrees
+  of crosslinking. For that reason we did not crosslink all systems tested, but only the most
+  promising structure. We show that crosslinking does not significantly 
+  change any of our drawn conclusions in Section ~\ref{section:xlink}.
+
+  \subsection{Equilibrium Calculations}
 
@@
 
-  \section*{Results and Discussion}
-
-  \subsection*{Determination of Nanoscopic Structural Details}
-
-  We will now address the questions raised in the introduction in the order
-  that they were asked.  %BJC: Not a fan of this transition
-
-  The simulations best support a model built with 5 monomers per layer based on
-  the measured pore-to-pore distances. To discern the composition of the
-  monomer layers, addressing (\ref{point:monomernum}), we ran simulations of
+  \section{Results and Discussion}
+
+%  \subsection{Determination of Nanoscopic Structural Details}
+  \subsection{Determining the Spatial Configuration of Monomers}
+
+  Our simulations best support a model built with 5 monomers per layer based on
+  the measured equlibrated pore-to-pore distances. To discern the composition of
+  the monomer layers, addressing (\ref{point:monomernum}), we ran simulations of
   systems created with 4 - 8 monomers per layer. Systems were built in both the
-  parallel displaced and sandwiched configurations and prepared according to the
-  dry equilibration procedure. All systems are stable after 400 ns of simulation.
-  In a sense, all systems are at least metastable, addressing
-  \ref{point:metastable}, however not all will make physical sense or fit the
-  experimental profile that we are looking to match. Figure ~\ref{fig:p2p}
-  shows the pore spacing for all systems tested. Systems built with 5 monomers in
-  each layer equilibrate to a pore spacing that is most consistent with the
+  parallel displaced and sandwiched configurations with layers initially spaced
+  3.7 \AA~ apart. Equilibrated configurations were prepared according to the dry
+  equilibration procedure. All systems are stable after 400 ns of simulation. In
+  a sense, all systems are at least metastable, addressing
+  (\ref{point:metastable}), however not all will make physical sense or fit the
+  experimental profile that we are looking to match. Figure~\ref{fig:p2p} shows
+  the pore spacing for all systems tested. Systems built with 5 monomers in each
+  layer equilibrate to a pore spacing that is most consistent with the
   experimental value of 4.12 nm derived from SAXS measurements
@@
   We learned that layers are well-defined and persistent, answering
-  (\ref{point:layers}). We verified our conclusion by plotting the pair
+  (\ref{point:layers}). We established our conclusion by plotting the pair
   correlation function, $g(z)$ calculated between atoms along the length of the
-  pores (Fig~\ref{fig:zdf}). We measured $g(z)$ with respect to aromatic rings in
+  pores (Fig.~\ref{fig:zdf}). We measured $g(z)$ with respect to aromatic rings in
   the head groups and, separately, with respect to carbon atoms in the alkane
-  chains. We see that sandwiched configuration layers stack 4.39 \angstrom apart
-  while parallel displaced configuration layers stack 4.38 \angstrom apart.  The
-  power spectrums used to calculate the reported layer spacings are given in the
-  Supplemental Information.
-
- \begin{figure}
-	\centering
-	\includegraphics[width=0.5\linewidth]{p2p.png}
+  chains. Using a fourier transform of $g(z)$, we see that sandwiched
+  configuration layers stack 4.39 \angstrom apart while parallel displaced
+  configuration layers stack 4.38 \angstrom apart.
+
+  \begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{p2p.png}
 	\caption{The pore spacing (given in nm) of the model increases as
@@
 	per layer in a parallel displaced configuration result in a pore spacing
-	closest to the experimental 4.12 nm}~\label{fig:p2p}
-  \end{figure}
-
-  \begin{figure}
-        \centering
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf5layered.png}
+	closest to the experimental value of 4.12 nm}~\label{fig:p2p}
+  \end{figure}
+
+  \begin{figure}
+        \centering
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
                 \caption{}\label{fig:zdf_layered}
@@
                 \centering
-                \includegraphics[width=\textwidth]{zdf5offset.png}
+                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
                 \caption{}\label{fig:zdf_offset}
@@
         parallel displaced configurations. Clear periodic maxima in the
-        $z$ probability density indicate distinct layers. The magnitude
+        $z$ number density indicate distinct layers. The magnitude
         of the spikes with respect to the average suggest that the 5
@@
   Simulated XRD of the sandwiched configuration contains all experimental
-  features except for R-helix. R-alkanes, R-spots and R-pores appear in the
+  features except for R-helix. R-alkanes, R-spots and R-pores appear close to their
   expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
-  a q value lower than experiment meaning the rings prefer to stack further
-  apart.
+  a q value lower than experiment meaning the head groups in our model prefer 
+  to stack farther apart.
 
@@
   relative to R-alkanes when compared to the sandwiched configuration. R-helix
-  appears apparently due to the parallel displaced aromatic rings
+  appears due to the parallel displaced aromatic rings. It is a subharmonic
+  of R-$\pi$ since the nearest vertically stacked head group to any given head
+  group is 7.4 \AA away.
 
@@
   reflections of interest to some degree}
-  \end{figure}
+  \label{fig:XRDsim}
+  \end{figure}
+
+%  In both simulated diffraction patterns R-alkanes appears in the expected location. 
+%  The location of R-pores is not well-defined in comparison to experiment. In order
+%  to resolve those reflections it would be necessary to simulate a much larger system, 
+%  but that is unnecessary since we can measure pore spacing manually as described 
+%  earlier. R-$\pi$ and R
+
+  In both the parallel displaced and sandwiched configurations, we noted that
+  R-$\pi$ appears in a location which corresponds to a real space separation
+  larger than experiment. We attribute this discrepancy to GAFF's inability to
+  appropriately model the aromatic interactions which would be necessary to
+  achieve the correct $\pi$-$\pi$ stacking distance. Systems have been modeled
+  that exhibit the correct stacking distance, however they are typically made of
+  planar molecules spanning a large area. The system we have modeled has bulky
+  tails whose entropic contributions compete with the $\pi$-$\pi$ stacking
+  interaction energy.  There have been efforts to model systems that contain
+  $\pi$ interactions in a classical mechanical context using polarizable
+  forcefields. We could implement a polarizable force field, however it is likely
+  not worth the extra computational cost. If our model proves to be inadequate
+  when simulating transport, we will revisit our current choice of forcefield.
 
@@
   the tilt angle of the alkane chains and showed that our system equilibrates to
-  an average tilt angle close to zero degrees ~\ref{fig:tilt}. To understand the
+  an average tilt angle close to zero degrees (Fig.~\ref{fig:tilt}). To understand the
   origin of the spots, we determined which atoms gave rise to the feature. Since
   R-spots is present as higher intensity spots within R-alkanes, it is likely
-  that the spots arise as a consequence of the tails. By removing atoms from the
+  that the spots arise as a consequence of the tails. By removing all non-tail atoms from the
   trajectory and simulating a diffraction pattern, we were able to isolate the
@@
   between each centroid and its nearest neighbors with respect to the plane of
-  the membrane (Figure~\ref{fig:centroids}).  %BJC: at one point Matt mention
-  doing a correlation function instead of just measuring the angles We see
-  distinct peaks in the distribution of these angles 
+  the membrane. We see distinct peaks in the distribution of these angles 
   (Figure~\ref{fig:tail_packing}).
@@
   patterns. We confirmed this conclusion by radially integrating the 2D WAXS
-  pattern for q values between 1.57 and 1.4 (real space between 4 and 4.5 \AA). We
+  pattern for $\left|\mathbf{q}\right|$ values between 1.57 and 1.4 (real space between 4 and 4.5 \AA). We
   observe that distinct peaks appear ca. 30 $\degree$, in close agreement with
   the previously measured angle distribution
-  (~\ref{fig:offset_integration}~\ref{fig:layered_integration}). We performed the
+  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We performed the
   same integration on the raw experimental data and found the angle at which
@@
         shows R-spots}\label{fig:tails}
-        %MRS2: might need to say how the dynamic range is adjusted here with only tails, since otherwise people will be confused with the R-spots being more intense. 
-	%BJC: what do you mean by dynamic range?
-	%BJC: Explain how colorbar is adjusted
-  \end{figure}
-
-  \begin{figure}
+  \end{figure}
+
+  \begin{figure}[!htb]
   \centering
@@
 		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
-		        \caption{}~\label{fig:rz_layered}
+		        \caption{}~\label{fig:layered_tails}
 		\end{subfigure}
@@
 
+  \subsection{Initial Layer Spacing Affects System Equilibration}
+
 %  The $z$-direction correlation functions show that layers in our model prefer
 %  to stack further apart than 3.7 \angstrom as suggested by experiment.
-  When systems are built with layers stacked 5.0 \angstrom apart then equilibrated, 
-  we observe long-term stability of a qualitatively different configuration
-  suggesting that we have found another metastable free energy basin,
-  further corroborating \ref{point:metastable}. We studied this type of system in
-  both the parallel displaced and sandwiched configurations.
-
-  Structural properties are different when layers are initially spaced 5 \AA apart.
-  \begin{itemize}
-	\item In both configurations we observe a decrease in pore spacing along with an increase in the equilibrated distance between layers.
-	\item The simulated X-ray diffraction patterns differ particularly with reference to R-spots.
-	\item R-helix is still faintly visible in the parallel displaced and absent in the sandwiched simulated diffraction pattern implying that head groups maintain their initial ordering to a degree.
-	\item In both cases, R-spots is markedly different.
-	\item When layers stack too far apart, they do not exhibit hexagonal packing
-	\item The intensity within R-alkanes of the parallel displaced configuration is nearly uniform with slightly more concentrated intensity at the top and bottom.
-	\item The sandwiched configuration possesses higher intensity regions at the top and bottom of R-alkanes as well as along the equator with high intensity near q$_z$ = 0.
-  \end{itemize}
-
-  \begin{figure}
-        \centering
+  When systems are built with layers stacked 5.0 \AA~ apart then
+  equilibrated, we observe long-term stability of a qualitatively different
+  configuration suggesting that we have found another metastable free energy
+  basin, further corroborating (\ref{point:metastable}). We studied this type of
+  system in both the parallel displaced and sandwiched configurations.
+
+  Structural properties are different when layers are initially spaced 5 \AA~
+  apart. In both configurations, we observe a decrease in pore spacing
+  (Fig.~\ref{fig:p2p_disordered}) and a corresponding increase in the equilibrated
+  distance between layers (Fig.~\ref{fig:dbwl_disordered}). The simulated X-ray
+  diffraction patterns indicate further structural differences. In the parallel
+  displaced configuration, R-spots fades to the point that it is indistinguisable
+  from R-alkanes (Fig. ~\ref{fig:offset_disordered_xrd}). In the sandwiched
+  configuration, R-spots is present in different locations, showing higher
+  intensity at the top and bottom of the pattern as well as at the intersection
+  of R-alkanes with q$_z$ = 0 (Fig. ~\ref{fig:layered_disordered_xrd}).
+
+  Neither assembly deviates from its initial head group arrangement. R-helix is still 
+  faintly visible in the parallel displaced configuration and is absent in the 
+  sandwiched simulated diffraction pattern. The spectroscopic signatures are unique to
+  the two different head group configurations.
+
+  \begin{figure}[!hbt]
+        \centering
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{dbwl.png}
+                \caption{}~\label{fig:dbwl_disordered}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{p2p2.png}
+                \caption{}~\label{fig:p2p_disordered}
+        \end{subfigure}
         \begin{subfigure}{0.45\linewidth}
@@
                 \caption{}~\label{fig:layered_disordered_xrd}
-        \end{subfigure}
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{dbwl.png}
-                \caption{}~\label{fig:dbwl_disordered}
-        \end{subfigure}%
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{p2p2.png}
-                \caption{}~\label{fig:p2p_disordered}
         \end{subfigure}
@@
 
-  In order to address \ref{point:poredefinition}, we plotted the number of
-  densities of heavy atoms in the head group and tail regions of the monomers in
-  addition to the sodium ions. (See Supplemental Information for definition of
-  head group and tail regions). For the head group region, we used the carbon
-  atoms making up the aromatic ring For the tail regions we used only carbon
-  atoms of the monomer tails
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.55\textwidth}
+  \subsection{Pore Structure Depends on Initial Configuration}
+
+  In order to address (\ref{point:poredefinition}), we plotted the number of
+  densities of heavy atoms in the head group, carbon atoms in the tail region
+  and the sodium ions (Figure~\ref{fig:densities}). For the head group region,
+  we used the carbon atoms making up the aromatic ring. For the tail region we
+  used only carbon atoms of the monomer tails (See Supplemental Information for
+  diagram). Histograms are average over at least 50 ns of equilibrated trajectory.
+
+  In all cases, the space in the pore region is filled with sodium ions and
+  head groups. There is a clear partition between the hydrophobic and hydrophilic
+  regions. Alkane tails do not cross into the pore region. We expect that when 
+  water is introduced to the system, water molecules will occupy the hydrophilic region
+  and open up the pores for aqueous solute transport.
+
+  The sandwiched configuration (Fig.~\ref{fig:layered_density}) shows a relatively
+  ordered pore structure. The number densities of components in all other
+  configurations are comparable. In contrast, sodium ions and head groups in the
+  sandwiched configuration are highly concentrated away from the pore center
+  meaning that there is vacancy in the pore region. A vacant pore is very likely
+  to be unstable in a real system, further supporting the physical realism of the
+  parallel displaced configuration.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
         \includegraphics[width=1\linewidth]{offset_density.png}
@@
   \end{subfigure}
-  \begin{subfigure}{0.55\textwidth}
+  \begin{subfigure}{0.45\textwidth}
         \includegraphics[width=1\linewidth]{layered_density.png}
         \caption{}
-        \label{fig:offset_density}
-  \end{subfigure}
-  \begin{subfigure}{0.55\textwidth}
+        \label{fig:layered_density}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
+        \caption{}
+        \label{fig:disordered_offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
         \includegraphics[width=1\linewidth]{disordered_density.png}
         \caption{}
-        \label{fig:offset_density}
-  \end{subfigure}
-  \caption{(a) Parallel Displaced (b) Sandwiched (c) ``Disordered''}~\label{fig:densities}
-  \end{figure}
-
-  % BJC: necessary to show layered configurations at this point?
+        \label{fig:disorder_layered_density}
+  \end{subfigure}
+  \caption{In all cases, assemblies stay partitioned into hydrophilic and
+	  hydrophobic regions. The parallel displaced (a), the disordered parallel
+	  displaced (c), and the disordered sandwiched (d) show similar pore structures.
+	  The sandwiched configuration (b) exhibits an open pore structure with sodium
+	  ions and head groups concentrated away from the pore
+	  center.}~\label{fig:densities}
+  \end{figure}
+
+  \subsection{Affect of Water on Structure}
+
+  % BJC: Is it necessary to show layered configurations at this point?
   We answered (\ref{point:water}) and further support (\ref{point:orientation})
@@
   wet equilibration procedure. There is no experimental measurement of trace
-  water concentration in the pores. We tested a range of water concentrations
+  water concentration in the pores so we tested a range of water concentrations
   from 0.5 to 5 percent. Our lower bound models a system with on average 2 water
   molecules for each monomer layer. Figure ~\ref{fig:solvation} shows the
-  simulated diffraction patters resulting from each configuration.
+  simulated diffraction patterns resulting from each configuration.
 
@@
         %MRS2: include 0% as well? Maybe leave off 5% if not relevant in the end?
+	\caption{}
 	\label{fig:solvation}
@@
   systems. The intensity of the reflections decrease when water is added to the
-  system. In systems built with 5 weight percent water, R-$\pi$ and R-spots
+  system. In systems built with 5 wt \% water, R-$\pi$ and R-spots
   become nearly indistinguishable from R-alkanes.
 
-%MRS3: is this point the right ``main'' thesis to make?
-I thought it was a more simple statement of being interested as to how water affected the structure.
-FYI, would be interesting to see the RDF's of the pores with and without water, BUT I think that's not necessary for this paper, that's more a 2nd paper thing.
-%MRS3: we didn't really test if water is  needed to obtain the structures; clearly, w/o water it's metastable for a long time.  We don't need the water simulations to prove this.  
-  Water is not needed to obtain and simulate the correct equilibrium 
-  membrane structure.
-  \begin{itemize}
-	\item We note that water absorbed during membrane synthesis may
-        be present in far lower concentrations than those 
-        tested here.
-	\item We do not eliminate the possibility that water is necessary
-        in order to drive self-assembly. Studying the mechanisms of self assembly is
-	beyond the scope of this work.
-	\item However, once the system has formed the Col\textsubscript{h} 
-	phase, adding water only drives disorder in the structure
-	\item In the equilibrium configuration, if water exists, it is confined
-	to the pore region where there is no driving force for aggregation of 
-	water molecules. 
-	\item In the case of trace water, water molecules will be too sparse to
-	form a hydrogen bonding network.
-  \end{itemize}
-
-  \subsection*{Ionic conductivity calculation}
-
-  We use the equilibrated parallel displaced system to calculate ionic
+  % BJC: unsure where or if this paragraph fits
+  Water is not necessary to maintain an ordered pore structure. We do not
+  eliminate the possibility that water is necessary in order to drive
+  self-assembly, however, studying the mechanisms of self assembly is beyond the
+  scope of this work. According to our model, once the system has formed the
+  Col\textsubscript{h} phase, adding water only drives disorder of the pore
+  structure. In the true equilibrium configuration, if water exists, it is
+  primarily confined to the pore region where there is no driving force for
+  aggregation of water molecules. In the case of trace water, water molecules
+  will be too sparse to form a hydrogen bonding network.
+
+  In systems built with 5 wt~\% water, the pore region becomes filled with
+  water. We plotted the number density of components in this system and see that
+  the pores become a soup of water molecules and sodium ions (Fig.
+  \ref{fig:water_density}. This system is a closer representation of the
+  H\textsubscript{II} phase which is typically synthesized with ca. 8 wt \%
+  water. We believe that the hydrated membrane pores will be valuable for aqueous
+  separations. Further analysis of and transport within the H\textsubscript{II}
+  phase are left for future studies.
+
+  \begin{figure}
+  \centering 
+  \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=1\linewidth]{offset_solvated_density.png}
+        \caption{}
+        \label{fig:offset_solvated_density}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=1\linewidth]{layered_solvated_density.png}
+        \caption{}
+        \label{fig:layered__solvated_density}
+  \end{subfigure}
+  \caption{Water fills the membrane pores in the parallel displaced (a) and 
+  sandwiched (b) configurations. Sodium ions are distributed more uniformly 
+  in the sandwiched configuration.}
+  \label{fig:water_density}
+  \end{figure}
+
+  \subsection{Model Ionic Conductivity Measurements}
+
+  We used the equilibrated parallel displaced system to calculate ionic
   conductivity since its structure is the closest match to experiment. The model
   gives reasonable estimates of ionic conductivity when compared to experiment.
-  Calculated values of ionic conductivity obtained using the Nernst Einstein
+  Calculated values of ionic conductivity obtained using the Nernst-Einstein
   relation and Collective Diffusion model are compared in
@@
   however it is not feasible to do so with a large system. We will only use the
-  Nernst Einstein relation in future calculations of this type.
+  Nernst-Einstein relation in future calculations of this type.
 
@@
   10,000 times thicker than our simulated system. The thick film likely has
-  defects leading to non-contiguous pores and imperfect alignment. The 2D SAXS
-  pattern shows the small degree of tortuosity present in the system
-  (~\ref{fig:2DSAXS}). It has been shown that there is a large dependence of
-  ionic conductivity on the alignment of the pores. The ionic conductivity of an
-  unaligned film is ca. 85 times lower than that of a nearly aligned film
-  referenced here. We hypothesize that a thin, perfectly aligned film would have
-  a value of ionic conductivity in agreement with our model
+  defects leading to non-contiguous pores and imperfect alignment.  It has been
+  shown that there is a large dependence of ionic conductivity on the alignment
+  of the pores. The ionic conductivity of an unaligned film is ca. 85 times lower
+  than that of a nearly aligned film referenced here. We hypothesize that a thin,
+  perfectly aligned film would have a value of ionic conductivity in agreement
+  with our model.
 
@@
 
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\linewidth]{2D-SAXS_cropped.png}
-  \caption{Experiments confirm that the pores have a small degree of tortuosity. 
-  The experimental two dimensional SAXS pattern exhibits reflections
-  resulting from highly aligned pore regions. A perfectly aligned system 
-  would exhibit sharp dots at the same locations of the refelctions shown. 
-  An isotropically aligned system the reflections would appear as 
-  rings centered about the origin}~\label{fig:2DSAXS}
-  \end{figure}
-
-  \subsection*{Implementation of the crosslinking algorithm}
-
-  We applied the crosslinking algorithm to the equilibrated parallel-displaced  
-  configuration with 5 monomers per layer.
-  \begin{itemize}  %BJC: working on the following. The following is what I expect
-%  	\item There is an even distribution of crosslinks between same monomer tails, 
-%	between monomers in the same pore and between monomers in different pores 
-%	including periodic boundaries.  % BJC: might leave this detail in the supplemental
-	\item We reach 95 \% conversion of terminal vinyl groups % BJC: we'll see
-	\item The distance between pores shrinks by 0.4\angstrom~ after the system is 
-	crosslinked  
-	\item We simulated the crosslinked system in the NPT ensemble for 100 ns
-	\item Major features are still present in the X-ray diffraction, however at lower intensities ~\ref{fig:rzplot_xlink} 
-	\item The ionic conductivity is lower in the crosslinked system ~\ref{fig:ic_xlink} % BJC: Nernst-Einstein is lower.
-Need a longer simulation to check Collective-Diffusion - I can probably avoid that by saying that we will be sticking with the Nernst-Einstein method
-  \end{itemize}
+  \subsection{Affect of Crosslinking}\label{section:xlink}
+
+  The system's structure and physical characteristics did not change
+  significantly when we applied the crosslinking algorithm to the equilibrated
+  parallel-displaced configuration built with 5 monomers per layer. We simulated
+  the crosslinked system in the NPT ensemble for 100 ns. The distance between
+  pores shrinks by 0.4 \angstrom~ after the system is crosslinked. All major
+  features are still present in the X-ray diffraction, however at lower
+  intensities (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using
+  the Nernst-Einstein relation and found that it is lower in the crosslinked
+  system (Fig.~\ref{fig:IC_xlink}).
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{ic_xlink.png}
-	\caption{}~\label{fig:ic_xlink}
+	\includegraphics[width=\textwidth]{IC_xlink.png}
+	\caption{}~\label{fig:IC_xlink}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{dbwl_xlink.png}
+	\caption{}~\label{fig:dbwl_xlink}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{p2p_xlink.png}
+	\caption{}~\label{fig:p2p_xlink}
   \end{subfigure}
@@
   system. (b) The ionic conductivity is smaller relative to the uncrosslinked system, but
-  still much larger than the experimental value}~\label{fig:xlink}
-  \end{figure}
-
-  \section*{Conclusion}
+  still much larger than the experimental value. (c) The distance between layers increases
+  when the system is crosslinked. (d) The pore spacing decreases when the membrane is 
+  crosslinked.}~\label{fig:xlink}
+  \end{figure}
+
+  \section{Conclusion}
 

### 2017-12-15 HII/Scripts/regional_density.py

@@ -20,6 +20,8 @@ def initialize():
     parser.add_argument('-bins', default=100, type=int, help='Number of bins to use')
     parser.add_argument('-m', '--multi', nargs='+', help='Overlay the density of each region with the results from '
                                                          'other trajectories')
+    parser.add_argument('-s', '--solvate', action="store_true",
+                        help='If the system is solvated, plot the number density of water as well')
 
     args = parser.parse_args()
 
@@ -107,6 +109,20 @@ if __name__ == "__main__":
 
     results = np.zeros([len(regions), args.bins])
 
+    keep = [a.index for a in t.topology.atoms if a.residue.name != 'HOH']  # everything kept if system not solvated
+
+    p_centers = physical.avg_pore_loc(npores, t.xyz[:, keep, :])
+
+    if args.solvate:
+
+        print('Calculating number density of solvent')
+        keep = [a.index for a in t.topology.atoms if a.residue.name == 'HOH' and a.name == 'O']
+        pos = t.xyz[:, keep, :]
+        p = duplicate(pos, t.unitcell_vectors)
+        equil = 0
+        density, r, bin_width = Structure_char.compdensity(pos, p_centers, equil, t.unitcell_vectors, pores=npores, buffer=0, nbins=args.bins)
+        plt.bar(r, density, bin_width, color='orange', alpha=0.5, label='Water')
+
     for i, reg in enumerate(regions):
 
         print('Calculating number density of %s region' % reg)
@@ -114,8 +130,6 @@ if __name__ == "__main__":
         pos = Structure_char.restrict_atoms(t, reg)  # restrict trajectory to region
 
         p = duplicate(pos, t.unitcell_vectors)  # duplicate things periodically
-
-        p_centers = physical.avg_pore_loc(npores, pos)
 
         equil = 0
         density, r, bin_width = Structure_char.compdensity(pos, p_centers, equil, t.unitcell_vectors, pores=npores, buffer=0, nbins=args.bins)
@@ -129,7 +143,7 @@ if __name__ == "__main__":
     plt.legend()
     plt.ylabel('Component Number Density (number/nm$^2$)')
     plt.xlabel('Distance from pore center (nm)')
-    plt.ylim([0, 0.6])
+    plt.ylim([0, 1.3])
     plt.tight_layout()
     plt.savefig("regional_density.png")
     plt.show()

### 2017-12-15 Ben_Manuscripts/structure_paper/Draft.tex
Raw WAXS integration

@@
   promising structure. We show that crosslinking does not significantly 
-  change any of our drawn conclusions in Section ~\ref{section:xlink}.
+  change any of our drawn conclusions in Section 3.6.
 
@@
   We explored the pore composition by measuring the average number densities of
-  various monomer components as a function of distance from the pore centers. The
-  centers of the pores were located using the same method used to calculate the
-  equilibrium pore spacing. We looked at the average number density of sodium
-  ions, aromatic rings and carbon atoms making up the monomer tails. The radial
-  distance of all atoms in each group from the pore centers are binned, then
-  normalized by the volume of the annulus defined by the bin edges and z box
-  vector.
+  various monomer components as a function of distance from the pore centers.  We
+  looked at the average number density of sodium ions, aromatic rings and carbon
+  atoms making up the monomer tails. The radial distance of all atoms in each
+  group from the pore centers are binned, then normalized by the volume of the
+  annulus defined by the bin edges and z box vector.
   %BJC: Maybe write an equation here? It's hard to say precisely how I did it
@@
   diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann constant,
-  $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$. 
+  $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$ 
   Sodium ion diffusion coefficients were found by calculating the slope
   of the linear region of the z-direction mean square displacement curve as
-  indicated by the einstein relation \cite{einstein_investigations_1956}.] We
-  looked at the MSD plot to determine where to begin and end a linear fit. Ion
+  indicated by the einstein relation \cite{einstein_investigations_1956}. We
+  visualized the MSD plot to determine where to begin and end a linear fit. Ion
   concentration was measured with respect to the volume of the entire unit cell.
 
-  The second method, termed the 'Collective Diffusion' model, measures the
+  The second method, termed the Collective Diffusion model, measures the
   movement of the collective variable, Q, which is defined as the amount of
@@
   of charge of the system. The conductance, $\gamma$ of the system can be
-  calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$. Conversion to ionic
+  calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic
   conductivity is achieved by multiplying by channel length and dividing by the
@@
   Our simulations best support a model built with 5 monomers per layer based on
-  the measured equlibrated pore-to-pore distances. To discern the composition of
+  the measured equilibrated pore-to-pore distances. To discern the composition of
   the monomer layers, addressing (\ref{point:monomernum}), we ran simulations of
@@
   parallel displaced and sandwiched configurations with layers initially spaced
-  3.7 \AA~ apart. Equilibrated configurations were prepared according to the dry
+  3.7 \AA~apart. Equilibrated configurations were prepared according to the dry
   equilibration procedure. All systems are stable after 400 ns of simulation. In
@@
 
+  \begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{p2p.png}
+	\caption{Systems built with 5 monomers per layer in a parallel
+		displaced configuration result in a pore spacing closest to the experimental
+		value of 4.12 nm. The pore spacing of the model increases as number of monomers
+		in each layer increases. The pore spacing of a system starting in the
+		sandwiched configuration is systematically lower than that started in an offset
+		configuration. }~\label{fig:p2p}
+  \end{figure}
+
   We learned that layers are well-defined and persistent, answering
   (\ref{point:layers}). We established our conclusion by plotting the pair
-  correlation function, $g(z)$ calculated between atoms along the length of the
+  correlation function, $g(z)$, calculated between atoms along the length of the
   pores (Fig.~\ref{fig:zdf}). We measured $g(z)$ with respect to aromatic rings in
@@
   chains. Using a fourier transform of $g(z)$, we see that sandwiched
-  configuration layers stack 4.39 \angstrom apart while parallel displaced
-  configuration layers stack 4.38 \angstrom apart.
-
-  \begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{p2p.png}
-	\caption{The pore spacing (given in nm) of the model increases as
-	number of monomers in each layer increases. The pore spacing of a system
-	starting in the sandwiched configuration is systematically lower than 
-	that started in an offset configuration. Systems built with 5 monomers
-	per layer in a parallel displaced configuration result in a pore spacing
-	closest to the experimental value of 4.12 nm}~\label{fig:p2p}
-  \end{figure}
+  configuration layers stack 4.39 \angstrom~ apart while parallel displaced
+  configuration layers stack 4.38 \angstrom~ apart.
 
@@
   trajectory after equilibration. The patterns for both structures are shown and
-  compared to experiment in Figure ~\ref{fig:XRDsim}.
+  compared to experiment in Figure \ref{fig:XRDsim}.
 
@@
   expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
-  a q value lower than experiment meaning the head groups in our model prefer 
+  a $q_z$ value lower than experiment meaning the head groups in our model prefer 
   to stack farther apart.
@@
   of R-$\pi$ since the nearest vertically stacked head group to any given head
-  group is 7.4 \AA away.
+  group is 7.4 \AA~ away.
 
@@
 
-  The peaks in the tilt angle distribution are consistent with the location of
-  R-spots. The peaks of interest in Figures \ref{fig:offset_tails} and
-  \ref{fig:layered_tails} are located at $\pm$ 33 $\degree$ which is the same
+  The peaks in the nearest neighbor angle distribution are consistent with the
+  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
+  and \ref{fig:layered_tails} are located at $\pm$ 33 $\degree$ which is the same
   location where the highest intensity of spots are located on the simulated
   patterns. We confirmed this conclusion by radially integrating the 2D WAXS
-  pattern for $\left|\mathbf{q}\right|$ values between 1.57 and 1.4 (real space between 4 and 4.5 \AA). We
-  observe that distinct peaks appear ca. 30 $\degree$, in close agreement with
-  the previously measured angle distribution
-  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We performed the
-  same integration on the raw experimental data and found the angle at which
-  R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a
-  reconcilable difference with our simulated results.
+  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
+  and 4.5 \AA~ in real space). We observe that distinct peaks appear ca. 30
+  $\degree$, in close agreement with the previously measured angle distribution
+  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
+  performed the same integration on the raw experimental data and found the angle
+  at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which
+  is a reconcilable difference with our simulated results.
 
@@
 	\end{subfigure} 
-%MRS: 
   \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
@@
 %  to stack further apart than 3.7 \angstrom as suggested by experiment.
-  When systems are built with layers stacked 5.0 \AA~ apart then
+  When systems are built with layers stacked 5.0 \AA~apart then
   equilibrated, we observe long-term stability of a qualitatively different
@@
   used only carbon atoms of the monomer tails (See Supplemental Information for
-  diagram). Histograms are average over at least 50 ns of equilibrated trajectory.
+  diagram). Histograms are averaged over at least 50 ns of equilibrated trajectory.
 
@@
 
-  The sandwiched configuration (Fig.~\ref{fig:layered_density}) shows a relatively
+  The sandwiched configuration (Fig. \ref{fig:layered_density}) shows a relatively
   ordered pore structure. The number densities of components in all other
@@
   the pores become a soup of water molecules and sodium ions (Fig.
-  \ref{fig:water_density}. This system is a closer representation of the
+  \ref{fig:water_density}). This system is a closer representation of the
   H\textsubscript{II} phase which is typically synthesized with ca. 8 wt \%
@@
   than that of a nearly aligned film referenced here. We hypothesize that a thin,
-  perfectly aligned film would have a value of ionic conductivity in agreement
-  with our model.
+  perfectly aligned film would have a value of ionic conductivity in close 
+  agreement with our model.
 
@@
         values of ionic conductivity an order of magnitude higher than the experimental
-        value}
+        value.}
         \label{fig:conductivity}
@@
   the crosslinked system in the NPT ensemble for 100 ns. The distance between
-  pores shrinks by 0.4 \angstrom~ after the system is crosslinked. All major
-  features are still present in the X-ray diffraction, however at lower
-  intensities (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using
-  the Nernst-Einstein relation and found that it is lower in the crosslinked
-  system (Fig.~\ref{fig:IC_xlink}).
+  pores shrinks by 0.4 \angstrom~ and the distance between layers increases by
+  0.04 \AA~ after the system is crosslinked. All major features are still present
+  in the simulated XRD patterns, however at lower intensities
+  (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using the
+  Nernst-Einstein relation and found that it is lower in the crosslinked system
+  (Fig.~\ref{fig:IC_xlink}).
 
@@
   We have used a detailed molecular model of the Col\textsubscript{h} phase
-  formed by NA-GA3C11 in order to study its nanoscopic structure. While there
+  formed by Na-GA3C11 in order to study its nanoscopic structure. While there
   have been efforts to model formation of various liquid crystalline phases with
@@
   to examine their structure with the same level of detail presented here.
-  Evidence strongly supports that layers are composed of 5 monomers. We have
-  confirmed that monomers stay partitioned into layers. We have explored the
-  affect of two different $\pi$-$\pi$ stacking modes on the equilibrated membrane
-  strucure. Simulated diffration patterns generated from MD trajectories suggest
-  that the parallel-displaced configuration produces a structure with the closest
-  match to experiment. Finally, water is not needed to create well-definied pore
-  structures. Now that we have a good idea of what the membrane structure should
+  Evidence strongly supports that monomers stay partitioned into layers and that
+  each layer contains 5 monomers. We have explored the affect of two different
+  $\pi$-$\pi$ stacking modes on the equilibrated membrane strucure. Simulated
+  diffration patterns generated from MD trajectories suggest that the
+  parallel-displaced configuration produces a structure with the closest match to
+  experiment. Finally, water is not needed to create well-definied pore
+  structures.
+
+  Now that we have a good idea of what the membrane structure should
   look like, we will evaluate transport of various solutes within the system. We

### 2017-12-15 Ben_Manuscripts/structure_paper/Draft.tex
First draft pretty much done

@@
 
+  %BJC: TODO: Scalable vector graphic for monomer structure, make bigger. Convert .svg to .eps
+  %           Thicken slabs
+  %           Make pore region on slab (blue) bigger
+  %           Bump up atom sizes in atomistic render
   \begin{figure}
@@
 		\centering
-		%\includegraphics[width=\linewidth, trim={2.5cm 0 4cm 1.25cm}, clip]{WAXS_raw.png}
 		\includegraphics[width=\textwidth]{NaGA3C11.png}
@@
   monomer structure in solute transport and membrane design. Models resulting
-  from molecular dynamics simulations will provide the required level of detail.
+  from molecular dynamics simulations will provide the required level of detail (Fig. \ref{fig:detail}).
   We can directly observe solute transport and suggest governing mechanisms. We
@@
 
-  % BJC: improve this figure
+  % BJC: TODO: Make new rendering of wedges
+  %            Change color scheme 
   \begin{figure}
@@
 
+  %BJC: TODO: update colorbar
   \begin{figure}
@@
 
+  %BJC: TODO: reproduce figure in latex (or gimp?) with higher resolution arrows
   \begin{figure}
@@
 
+  The colorbars on all diffraction patterns are normalized relative to
+  R-alkanes. We calculated the average intensity within R-alkanes of the
+  experimental pattern, $I_{avg}$.  We exclude intensities within $\pm$
+  30\degree~of the $q_r=0$ axis, since the simulated patterns differ from
+  experiment in those regions (See Fig. \ref{fig:XRDsim}).  We multiplied $I_{avg}$
+  by a scaling factor of 2.5.  Intensities that appear in the experimental
+  pattern $\geq$ 2.5$*I_{avg}$ receive colorbar values of 1. The result of this
+  colorbar scaling method is shown in Figure \ref{fig:WAXS}. We apply the same
+  scaling method to the simulated patterns.
+
   % BJC: I think this figure belongs somewhere else
@@
 
+  %BJC: TODO: increase font size on legends
   \begin{figure}
@@
   The parallel displaced configuration results in a simulated XRD pattern with
-  the closest match to experiment. It produces the only pattern that exhibits
-  all major reflections. R-alkanes, R-pores and R-$\pi$ appear as they do in the
-  sandwiched configuration. R-spots appears, however with a lower intensity
-  relative to R-alkanes when compared to the sandwiched configuration. R-helix
-  appears due to the parallel displaced aromatic rings. It is a subharmonic
-  of R-$\pi$ since the nearest vertically stacked head group to any given head
-  group is 7.4 \AA~ away.
-
+  the closest match to experiment. It produces the only pattern that exhibits all
+  major reflections. R-alkanes and R-pores appear as they do in the
+  sandwiched configuration. R-spots and R-$\pi$ appears, however with a lower intensity relative to
+  R-alkanes when compared to the sandwiched configuration. R-helix appears due to
+  the parallel displaced aromatic rings. It is a subharmonic of R-$\pi$ since the
+  nearest vertically stacked head group to any given head group is 7.4 \AA~ away.
+
+  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
   \begin{figure}
@@
         \centering
-        \vspace{0.25em}
-        \includegraphics[scale=0.0987]{WAXS_raw.png}
+%        \vspace{0.25em}
+        \includegraphics[scale=0.29]{WAXS_raw.png}
         \caption{}~\label{fig:raw_waxs}
@@
   \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
-  indicates an average tilt angle near 7\degree which is far from the 37\degree tilt angle 
-  previously used to explain R-spots}~\label{fig:tilt}
+  indicates an average tilt angle near 7\degree~which is far from the 37\degree~tilt angle 
+  previously used to explain R-spots.}~\label{fig:tilt}
   \end{figure}
@@
 	\end{subfigure}
-	\caption{(a) All atoms except carbon atoms making up the tails are removed from the 
-	trajectory. (b) The simulated diffraction pattern of the tail-only trajectory still 
-        shows R-spots}\label{fig:tails}
+	\caption{(a) All atoms except carbon atoms making up the tails are removed from a 
+	sandwiched configuration trajectory. (b) The simulated diffraction pattern of the
+        tail-only trajectory still shows R-spots}\label{fig:tails}
   \end{figure}
@@
   diffraction patterns indicate further structural differences. In the parallel
-  displaced configuration, R-spots fades to the point that it is indistinguisable
-  from R-alkanes (Fig. ~\ref{fig:offset_disordered_xrd}). In the sandwiched
-  configuration, R-spots is present in different locations, showing higher
+  displaced configuration, almost all contrast between R-spots and R-alkanes is faded
+  (Fig. ~\ref{fig:offset_disordered_xrd}). In the sandwiched
+  configuration, R-spots is weakly present, but in different locations, showing higher
   intensity at the top and bottom of the pattern as well as at the intersection
@@
         \end{subfigure}
-	\caption{In comparison to systems built with 3.7 \AA initial layer spacing,  
+	\caption{In comparison to systems built with 3.7 \AA~ initial layer spacing,  
                 the simulated X-ray diffraction patterns of the parrallel displaced (a) and 
  		sandwiched (b) configurations are different when systems are built with 
- 		a 5 \AA initial layer spacing, most notably in the region bounded by R-alkanes.
+ 		a 5 \AA~ initial layer spacing, most notably in the region bounded by R-alkanes.
       		When layers are stacked further apart, the distance between layers increases (c)
@@
 
+  % BJC: TODO: Increase font size
+  %            Put insets in the figures that make it clear what configuration each represents
   \begin{figure}
@@
 
+  % BJC: TODO: reformat
+  %            adjust colorbar
   \begin{figure}
@@
 
+  %BJC: TODO: Bigger fonts
   \begin{figure}
@@
 
+  %BJC: add units
   \begin{figure}

### 2017-12-18 Ben_Manuscripts/structure_paper/Draft.tex
Comments added.

@@
 
+%MRS3: this is a little disconnected to the contents as well.  You want
+%the paper to explain the why of doing this research.  Paragraph gives background, but doesn't motivate.
+
   Current commercial RO membranes are thin film composite membranes with a
@@
   %BJC : I don't know that this paragraph fits.  
+  %MRS3: not really.
+Maybe take a look at Osuji's recent review (2016, I think) that addresses applications of nanostructured membranes and uses.
+Could rewrite the introduction to be more about the general possibilities of nanostructured membranes, not just desalination.
+It should be an introduction to what you will talk about in the paper, not to everything related.
   Improved RO membranes can make desalination more sustainable. Only 0.5 \% of
@@
 
+%MRS3: I think that this paragraph probably should be couched in terms of what they COULD do, since are not widely used yet.
+%MRS3: if talking about existing membranes, should cite performance.
   Nanostructured membranes can bypass many of the performance issues which
@@
   act as a pore for aqueous separations.  One can envision tailoring the pore
-  region for specific separations by changing the monomer chemsitry.
+  region for specific separations by changing the monomer chemistry.
 
@@
 	hydrophilic head groups (blue) facing towards the disk center. The disks
-	assemble into hexagonally packed columnnar mesophases (e)}~\label{fig:assembly}
+	assemble into hexagonally packed columnar mesophases (e)}~\label{fig:assembly}
   \end{figure}
@@
   offers no insight into dynamics within the pore. In a later study of rejection
-  performance, it was shown that membranes formed by Na-GA3C11 can not perform
+  performance, it was shown that membranes formed by Na-GA3C11 
+%can not 
+  cannot perform
   separations of solutes less than 1.2 nm in diameter because the pores are too
@@
   A molecular level understanding of LLC membrane structure, enabled by
-  molecular dynamics simulations, will provide guidelines to reduce the large
+  molecular dynamics simulations, 
+%MRS3: suggest can provide, since we think it likely but cannot prove.
+%will 
+  can provide guidelines to reduce the large
   chemical space available to design monomers for creation of separation-specific
@@
 	\end{subfigure}
-  \caption{(a) Our previous understanding of the pore structure allows us to speculate
-	   about separation behavior. (b) A detailed molecular model will allow us to
+%MRS3: tweaked
+%  \caption{(a) Our previous understanding of the pore structure allows us to speculate
+%	   about separation behavior. (b) A detailed molecular model will allow us to
+%	   directly observe solute transport. Here, four stacked layers of 5 monomers
+%           are pictured atomistically. The hydrophilic region is in red and the 
+%	   hydrophobic region is colored blue.}~\label{fig:detail}
+  \caption{Our previous level of understanding of the pore structure (a) only allows us to speculate
+	   about transport behavior in the pore. A detailed molecular model (b) will allow us to
 	   directly observe solute transport. Here, four stacked layers of 5 monomers
-           are pictured atomistically. The hydrophilic region is in red and the 
-	   hydrophoic region is colored blue.}~\label{fig:detail}
+           are pictured from atomistic simulations. The hydrophilic region is in red and the 
+	   hydrophobic region is colored blue.}~\label{fig:detail}
   \end{figure}
@@
   are extremely electron withdrawing.
+%MRS3: perhaps ``in this study, we compare'', since the rest of the paper does not take place 
+in the the future of the author. Apply throughout the paper.
   \cite{waller_hybrid_2006,ringer_effect_2006}. We will compare simulated X-ray
-  diffration patterns to experiment in order to deduce which stacking 
+  diffraction patterns to experiment in order to deduce which stacking 
   configurations is most likely.
@@
   associated with a given LLC system. Simulating a membrane atomistically will
-  require many atoms which limits the timescales acessible with MD. It is
+%MRS3: rephrase.
+%  require many atoms 
+requires large systems
+which limits the timescales acessible with MD. It is
   reasonable to expect that we will generate configurations which are kinetically
@@
   use simulated X-ray diffraction patterns to see if there is any meaningful
-  structural difference between a "dry" and "wet" system.
+  structural difference between a ``dry'' and ``wet'' system.
 
@@
   %BJC: Would it be better to describe each reflection as a numbered list (like with the questions above?)
+  %MRS2: I like names better.
   We used experimental small-angle X-ray scattering (SAXS) data from
-  \cite{feng_thin_2016} (Fig. ~\ref{fig:SAXS}) and wide angle X-ray scattering
-  (WAXS) data (Fig. ~\ref{fig:WAXS}, produced as described in
+  %MRS3: note that ~ is a space, so you don't need to do Fig.~ ref.  The ~ keeps the Fig.~\ref together instead of being split over lines.
+  \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
+  (WAXS) data (Fig.~\ref{fig:WAXS}, produced as described in
   \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
@@
   five major features of interest present in the 2D experimental pattern shown in
-  Figure \ref{fig:WAXS}. The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
+  Figure \ref{fig:WAXS}. 
+%MRS3: break this into an enumerated list, rather than a wall of text.
+The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
   corresponding to a real space separation of 3.7 \angstrom~.  The reflection is
@@
   \angstrom~. This reflection has been interpreted as 2\textsubscript{1} helical
-  ordering of aromatic rings along the z axis meaning if the positions of the
+  ordering of aromatic rings along the z axis, meaning that if the positions of the
   aromatic rings can be traced by a helix, then for each full turn in the helix, one
@@
   higher relative intensity which will be called R-spots. All are located
-  $\approx 37$ degrees from the $q_z$ axis in their respective quadrants. In many
+  $\sim 37$ degrees from the $q_z$ axis in their respective quadrants. In many
   liquid crystal systems this can be explained by the tilt angle of the alkane
@@
 
+  %MRS3: this paragraph seems to be a little out of place: should go before a lot of the introductory material, since it lays out what you will be doing in the paper.
+
   In this study, we build a significantly more realistic atomistic model of LLC
@@
         \end{subfigure}
+%MRS; would be good to have all feature labels agree: either can edit to put the names on, or have a key relating numbers to the names you use.
 	\caption{(a) The repeat spacing in the 1D small angle X-ray scattering pattern
@@
   monomer. Monomers were cooled from 1000K to 50K over 10 nanoseconds.  A low
+%MRS3: need to describe this in more detail, but can be in the supplementary. 
   energy configuration was randomly pulled from the trajectory and charges were
-  reassigned using molcharge.  Using the new charges, the monomer system was
+  reassigned using molcharge.
+%MRS3: need to say what molcharge is.
+  Using the new charges, the monomer system was
   annealed again and a random monomer configuration was pulled from the
@@
   X-ray diffraction patterns. %This point will be explained in more detail later.
-
+%MRS3: isn't there some observations you need at least 10?  
 \subsection{Monomer Placement}
@@
   which leads to an artificially thick membrane with pores spaced closely
-  together. There will be no further discussion of this system but the interested
-  reader can learn more about it in the supplemental information.
+  together. 
+  Further details of simulations with large layer spacing are in the supplemental information.
+%There will be no further discussion of this system but the interested
+%  reader can learn more about it in the supplemental information.
 
@@
   equilibrium stacking distance ~\cite{sinnokrot_estimates_2002} is inconsistent
-  with R-$\pi$. It is also unfeasible for the monomers to orient in the T-shaped
+  with R-$\pi$. It is also infeasible for the monomers to orient in the T-shaped
   conformation because of the bulky tail groups. The system's preference towards
@@
   sandwiched or parallel-displaced configuration using position restraints with a
-  force constant of 1e6 KJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in the
+  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in the
   NVT ensemble which allows the monomer tails to settle without disrupting the
@@
   the square root of its previous value. Once the force constant is below 10 KJ
-  mol$^{-1}$ nm$^{-2}$, the restraints are released linearly until there is no more
-  restraining potential. The resulting unrestrained structure is allowed to
+  mol$^{-1}$ nm$^{-2}$, the restraints are released linearly 
+%MRS3: be more precise? you could reduce it from 10 in steps of 0.000001 kJ/mol, and that would be linear.
+%until there is no more
+%  restraining potential. 
+until the restraining potential is zero.
+The resulting unrestrained structure is allowed to
   equilibrate for 5 ns in the NPT ensemble with pressure controlled by the
   berendsen barostat. Next, we run long NPT equilibration simulations for at
-  least 400 ns using the Parrinello-Rahman barostat with a time consant of 10 ps.
+  least 400 ns using the Parrinello-Rahman barostat with a time constant of 10 ps.
 
   In order to create a wet system, we solvated an initial configuration with
-  water using gmx solvate. All water molecules placed outside the pore region are
+  water using \texttt{gmx solvate}. All water molecules placed outside the pore region are
   removed. Waters inside the pore region are randomly removed until the desired
@@
   only propagation mode considered due to its dominance in the real system.
+%MRS3: citation why it dominates the real system. 
   Direction of attack was not considered because the resultant mixture is
@@
 
-  Our implementation requires long simulation times to achieve high degrees
+  Our implementation requires long simulation times 
+%MRS3: specify long.  2 days?  2 months?
+to achieve high degrees
   of crosslinking. For that reason we did not crosslink all systems tested, but only the most
@@
   equilibrated based on when the distance between pores stops changing.
+%MRS: how did you determine when it stopped changing?  What statistical tests? By eye?
 
@@
   trajectory and then normalized by the average number density. To extract the
-  average distance between layers we applied a discrete fourier transform to
+  average distance between layers we applied a discrete Fourier transform to
   $g(z)$ and extracted the highest intensity frequency.
@@
   coordinates in order to make a direct experimental comparison. All atomic
-  coordinates were simulated as gaussian spheres of electron density
-  corresponding to each atom's atomic number. A three dimensional fourier
+  coordinates were simulated as Gaussian spheres of electron density
+  corresponding to each atom's atomic number. A three dimensional Fourier
   transform (FT) of the array of electron density results in a three dimensional
@@
   30\degree~of the $q_r=0$ axis, since the simulated patterns differ from
+%MRS3: provide a little more information: because we think that the alkane-alkane density, averaged over angles, is the feature most likely to be replicated between experiment and simulation, rather than something like the peaks,  We have to leave out the very top and bottom because simulation places the Pi-stacking reflection in the middle of the alkane band.
   experiment in those regions (See Fig. \ref{fig:XRDsim}).  We multiplied $I_{avg}$
-  by a scaling factor of 2.5.  Intensities that appear in the experimental
+  by a scaling factor of 2.5.  
+  %MRS3: why 2.5? To match what? Need to explain.
+Intensities that appear in the experimental
   pattern $\geq$ 2.5$*I_{avg}$ receive colorbar values of 1. The result of this
@@
   The Nernst-Einstein relation relates the DC ionic conductivity to ion
-  diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann constant,
+  diffusivity, $D$, concentration, $C$, ion charge, $q$, the Boltzmann constant,
   $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$ 
@@
   of the linear region of the z-direction mean square displacement curve as
-  indicated by the einstein relation \cite{einstein_investigations_1956}. We
+  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
   visualized the MSD plot to determine where to begin and end a linear fit. Ion
@@
   membrane cross sectional area.  $D_Q$ is the diffusion coefficient of the
-  collective variable Q. It can be calculated using the einstein relation.  A
+  collective variable Q. It can be calculated using the Einstein relation.  A
   full derivation of the model can be accessed elsewhere 
@@
   the head groups and, separately, with respect to carbon atoms in the alkane
-  chains. Using a fourier transform of $g(z)$, we see that sandwiched
+  chains. Using a Fourier transform of $g(z)$, we see that sandwiched
   configuration layers stack 4.39 \angstrom~ apart while parallel displaced
@@
   $\pi$ interactions in a classical mechanical context using polarizable
-  forcefields. We could implement a polarizable force field, however it is likely
+  forcefields. 
+%MRS3: cite specific efforts on treatement if pi-stacking.
+We could implement a polarizable force field, however it is likely
   not worth the extra computational cost. If our model proves to be inadequate
@@
 
+%MRS3: maybe the ``R-spots'' signal, to get agreement in number for grammar. Check other instances.
   R-spots, which appears in both simulated XRD patterns, is a result of
@@
   location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
-  and \ref{fig:layered_tails} are located at $\pm$ 33 $\degree$ which is the same
+  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
   location where the highest intensity of spots are located on the simulated
@@
   pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
-  and 4.5 \AA~ in real space). We observe that distinct peaks appear ca. 30
-  $\degree$, in close agreement with the previously measured angle distribution
+  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
+  \degree$, in close agreement with the previously measured angle distribution
   (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
   performed the same integration on the raw experimental data and found the angle
-  at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which
+  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
   is a reconcilable difference with our simulated results.
@@
         tail-only trajectory still shows R-spots}\label{fig:tails}
+        %MRS3: so I didn't realize this before, but why are there still fairly significant peaks in the pi-stacking region when the head groups are removed?
+        %Do you feel you understand this? I suppose it is because the top of the tails must be correlated with the aromatic ring by covalent bonding?
   \end{figure}
@@
   equilibrated, we observe long-term stability of a qualitatively different
-  configuration suggesting that we have found another metastable free energy
+  configuration, suggesting that we have found another metastable free energy
   basin, further corroborating (\ref{point:metastable}). We studied this type of
@@
 
+%MRS3: specify which ones are referred to by neither.
   Neither assembly deviates from its initial head group arrangement. R-helix is still 
@@
 	\caption{In comparison to systems built with 3.7 \AA~ initial layer spacing,  
-                the simulated X-ray diffraction patterns of the parrallel displaced (a) and 
+                the simulated X-ray diffraction patterns of the parallel displaced (a) and 
  		sandwiched (b) configurations are different when systems are built with 
@@
   head groups. There is a clear partition between the hydrophobic and hydrophilic
-  regions. Alkane tails do not cross into the pore region. We expect that when 
+  regions. Alkane tails do not cross into the pore region. 
+%MRS3: this is a bit weird, since you carry out the water experiments in this study, so you don't have to expect anything.
+MAybe something like: We address later in the paper where water might partition in the pores''.
+We expect that when 
   water is introduced to the system, water molecules will occupy the hydrophilic region
@@
 
+%MRS3: maybe ``a more ordered pore structure''.  I wouldn't call any of them THAT ordered (it's really a judgement call), but the data certainly suggest sandwiched is more ordered than the others.
   The sandwiched configuration (Fig. \ref{fig:layered_density}) shows a relatively
@@
   sandwiched configuration are highly concentrated away from the pore center
-  meaning that there is vacancy in the pore region. A vacant pore is very likely
+  meaning that there is vacancy in the pore region. 
+%MRS3: weaken this conclusion, since we don't know for sure: ``less likely to be stable''. Don't need to qualify ``in a real system'', since the same destabilization effects will occur in both.
+A vacant pore is very likely
   to be unstable in a real system, further supporting the physical realism of the
@@
   \end{subfigure}
+%MRS3: I think it's a little more interesting, in that the pores clearly have hydrophobic and hydrophilic regions, but there is no abrupt transition.
+From 0.75 to 1.0 A, you have appreciable amounts of both moieties.
+And there isn't that much completely open sace.
+Sandwiched is a little more open.
+But if you look at the number density from 0.00 to 0.25, it's about the same, it just has less sodium in the tails.
+Interesting that the tail density is about the same for all of them.
+%MRS3: conclusions might be strenghtened if you could put in numbers (like integrated densitys (rememver 4pir^2 factor) of diffferet peaks in different regions.
   \caption{In all cases, assemblies stay partitioned into hydrophilic and
@@
   % BJC: Is it necessary to show layered configurations at this point?
+%MRS3: necessary for what point?
+%MRS3: remind peple what the structural points are, they don't want to go back.
   We answered (\ref{point:water}) and further support (\ref{point:orientation})
@@
   H\textsubscript{II} phase which is typically synthesized with ca. 8 wt \%
-  water. We believe that the hydrated membrane pores will be valuable for aqueous
+  water. 
+%MRS3: This next sentence is a little strange, since obviously we think it will be valuable from the introdiction; isn't really supporting data for this paragraph.
+We know that there are some selectivity features already.
+Maybe something like ``further analysis of water in these pores can help unravel the mechanisms for selective transport in separations of aqueous solutions?''.
+We believe that the hydrated membrane pores will be valuable for aqueous
   separations. Further analysis of and transport within the H\textsubscript{II}
@@
   sandwiched (b) configurations. Sodium ions are distributed more uniformly 
+%MRS3: more uniformly compared to what? parallel displaced, or previous sandwiched simulations?
   in the sandwiched configuration.}
@@
   than that of a nearly aligned film referenced here. We hypothesize that a thin,
-  perfectly aligned film would have a value of ionic conductivity in close 
+
+  perfectly aligned film would have a value of ionic conductivity in 
+%MRS3: changed:
+%close 
+closer
   agreement with our model.
@@
 
-  \subsection{Affect of Crosslinking}\label{section:xlink}
+  \subsection{Effect of Crosslinking}\label{section:xlink}
 
@@
 
+%MRS3: spend a bit more time explaining the findings to remind people what they are in a bit more detail.  Separate paragraph for each main finding.
   % add stuff about pore structure and 'disordered' basin once there are concrete results 
@@
   each layer contains 5 monomers. We have explored the affect of two different
-  $\pi$-$\pi$ stacking modes on the equilibrated membrane strucure. Simulated
-  diffration patterns generated from MD trajectories suggest that the
+  $\pi$-$\pi$ stacking modes on the equilibrated membrane structure. Simulated
+  diffraction patterns generated from MD trajectories suggest that the
   parallel-displaced configuration produces a structure with the closest match to
-  experiment. Finally, water is not needed to create well-definied pore
+  experiment. Finally, water is not needed to create well-defined pore
   structures.
 
+%MRS3: this is a little informal. Something like ``With the structural understanding gained by these simulations'' 
   Now that we have a good idea of what the membrane structure should
@@
 \end{document}
+
+% LocalWords:  Nanostructured desalination biorefinement solute RO NF bruggen
+% LocalWords:  polydisperse diffusivity solutes BJC ultrafiltration nanometer
+% LocalWords:  ionizable pretreatment Graphene solvated Na GA zhou resel feng
+% LocalWords:  ca wt mesophases al crosslinking THF nanoporous PDMS nanopores
+% LocalWords:  TODO svg eps atomistically counterion nanoscopic counterions XRD
+% LocalWords:  WAXS headgroups initio metastable timescales acessible leached
+% LocalWords:  SAXS alkane alkanes Antechamber bccsym molcharge QUACPAC Openeye
+% LocalWords:  Gromacs berendsen timescale Packmol xyz hydrophlic xy pd tshaped
+% LocalWords:  KJ NVT kJ Parrinello Rahman gmx solvate polymerization FRP FRPs
+% LocalWords:  crosslink binned DC MSD subharmonic matplotlib GAFF's xrd llc
+% LocalWords:  polarizable reconcilable screenshot crosslinked uncrosslinked

### 2017-12-19 Ben_Manuscripts/structure_paper/Draft.tex
revisions

@@
   they offer the ability to control membrane architecture at the atomic scale
-  permitting the design of solute-specific separation membranes.
-  \cite{humplik_nanostructured_2011} Most membrane-based aqueous separations of
+  permitting the design of solute-specific separation membranes
+  \cite{humplik_nanostructured_2011}. Most membrane-based aqueous separations of
   small molecules can be achieved using reverse osmosis (RO) or nanofiltration
@@
 
+  Current commercial RO and NF membranes suffer from inherent limitations of
+  their fabrication. Although scalable, each process has a degree of
+  stochasticity which makes overcoming the permeability-selectivity tradeoff a
+  challenge. Namely, it is difficult to increase the permeability of a desired
+  species, while maintaining the same retention of an undesired species.
+
+  Commercial RO membranes are thin film composite membranes with a porous
+  support layer and an active layer made of a polymer matrix formed by
+  interfacial polymerization of a diamine. During the membrane fabrication,
+  aqueous diamine solution is allowed to penetrate into the polysulfone support
+  layer which is then immersed in trimesoyl chloride, a compound that is
+  immiscible in water. Diamine polymerizes with trimesoyl chloride at the
+  solution interface and creates a thin film that physically adheres to the
+  polysulfone support. The polymer matrix is dense and highly crosslinked
+  which leads to low permeability.
+
+  NF membranes are typically made by a phase inversion process. During phase
+  inversion, a thin polymer film is precipitated out of a polymer solution.
+  Through the use of a non-solvent, a polymer-rich and polymer-poor phase is
+  formed. A membrane is created as the polymer-poor phase forms pores in the
+  polymer-rich phase. Resultant pores are polydisperse in size which hurts
+  membrane selectivity. A second technique used to create NF membranes is call
+  track etching in which a polymer film is bombarded with charged particles, then
+  chemically etched to create pores. The pores are uniform which benefits
+  selectivity, however the membrane has a low porosity and subsequent low
+  permeability.
+
 %MRS3: this is a little disconnected to the contents as well.  You want
@@
 
-  Current commercial RO membranes are thin film composite membranes with a
-  porous support layer and an active layer made of a dense polymer matrix. The
-  membranes are unstructured with tortuous and polydisperse diffusion pathways.
-  Separation occurs based on differences in solubility and diffusivity of solutes
-  within the polymer matrix \cite{wijmans_solution-diffusion_1995}. With
-  optimization, one can exploit these differences to create a functional
-  selective barrier. RO operation costs are suboptimal because high feed
-  pressures are required in order to achieve a useful solvent flux.
+%  Current commercial RO membranes are thin film composite membranes with a
+%  porous support layer and an active layer made of a dense polymer matrix. The
+%  membranes are unstructured with tortuous and polydisperse diffusion pathways.
+%  Separation occurs based on differences in solubility and diffusivity of solutes
+%  within the polymer matrix \cite{wijmans_solution-diffusion_1995}. With
+%  optimization, one can exploit these differences to create a functional
+%  selective barrier. RO operation costs are suboptimal because high feed
+%  pressures are required in order to achieve a useful solvent flux.
 
@@
 It should be an introduction to what you will talk about in the paper, not to everything related.
-  Improved RO membranes can make desalination more sustainable. Only 0.5 \% of
-  the world's water is fresh. Desalination is an important source of potable
-  water, necessary in order to keep up with demand generated by a rapidly growing
-  global population. Although RO is currently the cheapest form of desalination,
-  the cost must be further decreased in order to meet demand. A typical seawater
-  desalination process requires feed pressures in the range of 800 to 1000 psi
-  \cite{fritzmann_state---art_2007}. By designing better membranes for
-  desalination, we can achieve higher water fluxes and reduce feed pressure
-  requirements which will decrease the cost of fresh water production.
-  \cite{humplik_nanostructured_2011}.
+ % Improved RO membranes can make desalination more sustainable. Only 0.5 \% of
+ % the world's water is fresh. Desalination is an important source of potable
+ % water, necessary in order to keep up with demand generated by a rapidly growing
+ % global population. Although RO is currently the cheapest form of desalination,
+ % the cost must be further decreased in order to meet demand. A typical seawater
+ % desalination process requires feed pressures in the range of 800 to 1000 psi
+ % \cite{fritzmann_state---art_2007}. By designing better membranes for
+ % desalination, we can achieve higher water fluxes and reduce feed pressure
+ % requirements which will decrease the cost of fresh water production.
+ % \cite{humplik_nanostructured_2011}.
 
@@
 
-  NF was introduced as an intermediate between RO and ultrafiltration, having
-  the ability to separate organic matter and salts on the order of one nanometer
-  in size. Explicit pore pathways running through the thickness of the membrane
-  permit high solvent fluxes at lower pressures than RO. NF membranes typically
-  have a surface charge resulting from ionizable groups which affords separation
-  of ions smaller than the pore radius by the mechanism of Donnan exclusion
-  \cite{van_der_bruggen_review_2003}. NF is often used as a precursor to reverse
-  osmosis since it can efficiently remove a significant portion of dissolved
-  solutes. Following NF pretreatment, RO can further purify the permeate. 
-  Unfortunately, NF membranes, like RO, possess a pore size
-  distribution which limits their ability to perform precise separations
-  \cite{bowen_modelling_2002}. An NF membrane with high selectivity could offer
-  the versatility to separate ions as well as small charged and uncharged
-  molecules to the same degree as RO and at a significantly lower cost.
+  %NF was introduced as an intermediate between RO and ultrafiltration, having
+  %the ability to separate organic matter and salts on the order of one nanometer
+  %in size. Explicit pore pathways running through the thickness of the membrane
+  %permit high solvent fluxes at lower pressures than RO. NF membranes typically
+  %have a surface charge resulting from ionizable groups which affords separation
+  %of ions smaller than the pore radius by the mechanism of Donnan exclusion
+  %\cite{van_der_bruggen_review_2003}. NF is often used as a precursor to reverse
+  %osmosis since it can efficiently remove a significant portion of dissolved
+  %solutes. Following NF pretreatment, RO can further purify the permeate. 
+  %Unfortunately, NF membranes, like RO, possess a pore size
+  %distribution which limits their ability to perform precise separations
+  %\cite{bowen_modelling_2002}.
+
+  The permeability-selectivity tradeoff has the potential to be overcome by
+  designing membranes at the molecular level. Next-geneartion nanostructured
+  membranes with high selectivity permitted by a precisely controlled pore size
+  and high permeability allowed by its porous architecture, have the potential to
+  replace traditional RO and NF membrane technologies.
 
@@
 %MRS3: if talking about existing membranes, should cite performance.
-  Nanostructured membranes can bypass many of the performance issues which
-  plague traditional NF and RO membranes. One can accomplish targeted separations
-  with high selectivity by tuning shape, size and functionality of the molecular
-  building blocks which form these materials. As a result, solute rejecting pores
-  can have their sizes tuned uniformly, resulting in strict size cut-offs.
-  Entirely different mechanisms may govern transport in a given nanostructured
-  material which can inspire novel separation techniques.
+%  Nanostructured membranes can bypass many of the performance issues which
+%  plague traditional NF and RO membranes. One can accomplish targeted separations
+%  with high selectivity by tuning shape, size and functionality of the molecular
+%  building blocks which form these materials. As a result, solute rejecting pores
+%  can have their sizes tuned uniformly, resulting in strict size cut-offs.
+%  Entirely different mechanisms may govern transport in a given nanostructured
+%  material which can inspire novel separation techniques.
 
@@
   offers no insight into dynamics within the pore. In a later study of rejection
-  performance, it was shown that membranes formed by Na-GA3C11 
-%can not 
-  cannot perform
+  performance, it was shown that membranes formed by Na-GA3C11 cannot perform
   separations of solutes less than 1.2 nm in diameter because the pores are too
@@
 
+  %MRS3: this paragraph seems to be a little out of place: should go before a lot of the introductory material, since it lays out what you will be doing in the paper.
+  %BJC2: Paragraph moved up here from well below.
+  In this study, we build a significantly more realistic atomistic model of LLC
+  membranes than, to our knowledge, has ever previously been done, and explore
+  what new structural information can be gained and what structure hypotheses are
+  supported by this model. We validate the model using as much experimental
+  information as possible. We are most interested in reproducing the conclusions
+  about structure which have been drawn from X-ray diffraction (XRD) experiments
+  and in matching ionic conductivity measurements \cite{feng_thin_2016}.
+
   A molecular level understanding of LLC membrane structure, enabled by
-  molecular dynamics simulations, 
-%MRS3: suggest can provide, since we think it likely but cannot prove.
-%will 
-  can provide guidelines to reduce the large
+  molecular dynamics simulations, can provide guidelines to reduce the large
   chemical space available to design monomers for creation of separation-specific
@@
   monomer structure in solute transport and membrane design. Models resulting
-  from molecular dynamics simulations will provide the required level of detail (Fig. \ref{fig:detail}).
-  We can directly observe solute transport and suggest governing mechanisms. We
-  can observe how the choice of head group may influence pore size for size
-  exclusion driven separations. We can interchange counterions which may
-  influence both the pore size and the strength of the Donnan potential which
-  affects the degree to which the membrane can exclude charged species.
+  from molecular dynamics simulations will provide the required level of detail
+  (Fig. \ref{fig:detail}).  We can directly observe solute transport and suggest
+  governing mechanisms. We can observe how the choice of head group may influence
+  pore size for size exclusion driven separations. We can interchange counterions
+  which may influence both the pore size and the strength of the Donnan potential
+  which affects the degree to which the membrane can exclude charged species.
 
@@
 	\end{subfigure}
-%MRS3: tweaked
-%  \caption{(a) Our previous understanding of the pore structure allows us to speculate
-%	   about separation behavior. (b) A detailed molecular model will allow us to
-%	   directly observe solute transport. Here, four stacked layers of 5 monomers
-%           are pictured atomistically. The hydrophilic region is in red and the 
-%	   hydrophobic region is colored blue.}~\label{fig:detail}
   \caption{Our previous level of understanding of the pore structure (a) only allows us to speculate
@@
   investigate.
-% which will be laid out and numbered in subsequent paragraphs.
-
-  %BJC: commenting out :There has been no definitive answer in literature
-  %regarding the number of monomers in each layer.  MRS3: the intro to the list
-  %talks about only ``numbers of monomers in each layer'', whereas the list
-  %below talks about several questions relating to layers. Can you rephrase so
-  %it's more general? Maybe just take out that sentence above.
 
@@
   are extremely electron withdrawing.
-%MRS3: perhaps ``in this study, we compare'', since the rest of the paper does not take place 
-in the the future of the author. Apply throughout the paper.
-  \cite{waller_hybrid_2006,ringer_effect_2006}. We will compare simulated X-ray
-  diffraction patterns to experiment in order to deduce which stacking 
-  configurations is most likely.
+  \cite{waller_hybrid_2006,ringer_effect_2006}. In this study, we compare
+  simulated X-ray diffraction patterns to experiment in order to deduce which
+  stacking configurations is most likely.
 
@@
   There remains the possibility that there is more than one metastable state
-  associated with a given LLC system. Simulating a membrane atomistically will
-%MRS3: rephrase.
-%  require many atoms 
-requires large systems
-which limits the timescales acessible with MD. It is
+  associated with a given LLC system. Simulating a membrane atomistically
+  requires many atoms which limits the timescales acessible with MD. It is
   reasonable to expect that we will generate configurations which are kinetically
@@
 
-  %BJC: Would it be better to describe each reflection as a numbered list (like with the questions above?)
-  %MRS2: I like names better.
   We used experimental small-angle X-ray scattering (SAXS) data from
-  %MRS3: note that ~ is a space, so you don't need to do Fig.~ ref.  The ~ keeps the Fig.~\ref together instead of being split over lines.
   \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
@@
   Figure \ref{fig:WAXS}.
-%MRS3: break this into an enumerated list, rather than a wall of text.
-The first is located at $q_z$ = 1.7 \angstrom$^{-1}$,
-  corresponding to a real space separation of 3.7 \angstrom~.  The reflection is
-  attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
-  perpendicular to the membrane plane, or z-axis \cite{feng_scalable_2014}. For
-  simplicity, this reflection will be referred to as R-$\pi$. A weak intensity
-  line is located at exactly half the $q_z$ value of R-$\pi$ ($q_z$ = 0.85
-  \angstrom$^{-1}$), corresponding to a real space periodic spacing of 7.4
-  \angstrom~. This reflection has been interpreted as 2\textsubscript{1} helical
-  ordering of aromatic rings along the z axis, meaning that if the positions of the
-  aromatic rings can be traced by a helix, then for each full turn in the helix, one
-  will encounter two aromatic rings. For this reason it will be referred to as
-  R-helix. A third major reflection is marked by a low intensity ring located at
-  r = 1.4 \angstrom$^{-1}$. The real space separation corresponds to 4.5 \angstrom~
-  which is characteristic of the average spacing between packed alkane chains.
-  This reflection will be called R-alkanes. Within R-alkanes, are four spots of
-  higher relative intensity which will be called R-spots. All are located
-  $\sim 37$ degrees from the $q_z$ axis in their respective quadrants. In many
-  liquid crystal systems this can be explained by the tilt angle of the alkane
-  chains with respect to the membrane plane. The final feature corresponds to the
-  spacing and symmetry of the d\textsubscript{100} plane which can be related to
-  the distance between pores.  The feature, which will be called R-pores, is
-  characterized by dots along $q_z$ = 0. The spacing between dots is indicative
-  of the hexagonal symmetry of the packed pores. The same information at higher
-  resolution is obtained using a SAXS setup.
-
-  %MRS3: this paragraph seems to be a little out of place: should go before a lot of the introductory material, since it lays out what you will be doing in the paper.
-
-  In this study, we build a significantly more realistic atomistic model of LLC
-  membranes than, to our knowledge, has ever previously been done, and explore
-  what new structural information can be gained and what structure hypotheses are
-  supported by this model. We validate the model using as much experimental
-  information as possible. We are most interested in reproducing the conclusions
-  about structure which have been drawn from X-ray diffraction (XRD) experiments
-  and in matching ionic conductivity measurements \cite{feng_thin_2016}.
+
+  \begin{enumerate}
+
+  	\item The first is located at $q_z$ = 1.7 \angstrom$^{-1}$, corresponding to
+	a real space separation of 3.7 \angstrom~.  The reflection is attributed to
+	$\pi$-$\pi$ stacking between aromatic rings in the direction perpendicular to
+	the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
+	reflection will be referred to as R-$\pi$.
+
+  	\item A weak intensity line is located at exactly half the $q_z$ value of
+	R-$\pi$ ($q_z$ = 0.85 \angstrom$^{-1}$), corresponding to a real space periodic
+	spacing of 7.4 \angstrom~. This reflection has been interpreted as
+	2\textsubscript{1} helical ordering of aromatic rings along the z axis, meaning
+	that if the positions of the aromatic rings can be traced by a helix, then for
+	each full turn in the helix, one will encounter two aromatic rings. For this
+	reason it will be referred to as R-helix.
+
+	\item A third major reflection is marked by a low intensity ring
+	located at r = 1.4 \angstrom$^{-1}$. The real space separation corresponds to
+	4.5 \angstrom~ which is characteristic of the average spacing between packed
+	alkane chains.  This reflection will be called R-alkanes.
+
+	\item Within R-alkanes, are four spots of higher relative intensity
+	which will be called R-spots. All are located $\sim 37$ degrees from the $q_z$
+	axis in their respective quadrants. In many liquid crystal systems this can be
+	explained by the tilt angle of the alkane chains with respect to the membrane
+	plane.
+
+	\item The final feature corresponds to the spacing and symmetry of the
+	d\textsubscript{100} plane which can be related to the distance between pores.
+	The feature, which will be called R-pores, is characterized by dots along $q_z$
+	= 0. The spacing between dots is indicative of the hexagonal symmetry of the
+	packed pores. The same information at higher resolution is obtained using SAXS.
+
+  \end{enumerate}
 
@@
         \end{subfigure}
-%MRS; would be good to have all feature labels agree: either can edit to put the names on, or have a key relating numbers to the names you use.
+%MRS3: would be good to have all feature labels agree: either can edit to put the names on, or have a key relating numbers to the names you use.
+%BJC2: I will annotate it with the names R-pi, R-alkanes etc. Is that what you mean?
 	\caption{(a) The repeat spacing in the 1D small angle X-ray scattering pattern
@@
 %MRS3: need to describe this in more detail, but can be in the supplementary. 
+%BJC2: would it be best to include the parameterization script
   energy configuration was randomly pulled from the trajectory and charges were
@@
 %MRS3: need to say what molcharge is.
+%BJC2: I say in paragraph above : "Atomic charges were assigned using the am1bccsym method of 
+%molcharge shipped with QUACPAC from ...". Is that not enough?
   Using the new charges, the monomer system was
@@
   trajectory to be used for full system construction (Figure~\ref{fig:python}a).
+  See supplemental information for further detail.
 
@@
 %MRS3: isn't there some observations you need at least 10?  
+%BJC2: When I first set up the system, there was a gap and a small number of layers 
+% appeared to cause the phase to disassociate. However, I can get a pretty small
+% number of layers in the infinite pore system, but the diffraction is low resolution.
+
 \subsection{Monomer Placement}
@@
   sandwiched or parallel-displaced configuration using position restraints with a
-  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in the
-  NVT ensemble which allows the monomer tails to settle without disrupting the
-  ordering of the head groups. Doing so also mitigates system dependence on
+  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in
+  the NVT ensemble which allows the monomer tails to settle without disrupting
+  the ordering of the head groups. Doing so also mitigates system dependence on
   initial monomer configuration. Every 50 ps, we reduce the force constants by
   the square root of its previous value. Once the force constant is below 10 KJ
-  mol$^{-1}$ nm$^{-2}$, the restraints are released linearly 
-%MRS3: be more precise? you could reduce it from 10 in steps of 0.000001 kJ/mol, and that would be linear.
-%until there is no more
-%  restraining potential. 
-until the restraining potential is zero.
-The resulting unrestrained structure is allowed to
-  equilibrate for 5 ns in the NPT ensemble with pressure controlled by the
-  berendsen barostat. Next, we run long NPT equilibration simulations for at
-  least 400 ns using the Parrinello-Rahman barostat with a time constant of 10 ps.
+  mol$^{-1}$ nm$^{-2}$, the restraints are reduced in a sequence with values of
+  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. The resulting
+  unrestrained structure is allowed to equilibrate for 5 ns in the NPT ensemble
+  with pressure controlled by the berendsen barostat. Next, we run long NPT
+  equilibration simulations for at least 400 ns using the Parrinello-Rahman
+  barostat with a time constant of 10 ps.
 
   In order to create a wet system, we solvated an initial configuration with
-  water using \texttt{gmx solvate}. All water molecules placed outside the pore region are
-  removed. Waters inside the pore region are randomly removed until the desired
-  concentration of water in the pores is reached. The remainder of the
-  equilibration follows the same procedure as the dry system.
+  water using \texttt{gmx solvate}. All water molecules placed outside the pore
+  region are removed. Waters inside the pore region are randomly removed until
+  the desired concentration of water in the pores is reached. The remainder of
+  the equilibration follows the same procedure as the dry system.
 
@@
 %MRS3: citation why it dominates the real system.
+%BJC2: Yea. There are a few citations that I need to make. I know they exist
+% but I need to track them down. I've prioritized that last. 
   Direction of attack was not considered because the resultant mixture is
@@
 
-  Our implementation requires long simulation times 
-%MRS3: specify long.  2 days?  2 months?
-to achieve high degrees
-  of crosslinking. For that reason we did not crosslink all systems tested, but only the most
-  promising structure. We show that crosslinking does not significantly 
+  Our implementation requires long simulation times to achieve high degrees of
+  crosslinking. A typical crosslinking procedure can take up to 24 hours. In
+  order to collect equilibrated data, further NPT simulation is necessary. We
+  typically run a crosslinked system for an additional 100 ns to allow the system
+  to readjust. For those reasons we did not crosslink all systems tested, but only
+  the most promising structure. We show that crosslinking does not significantly
   change any of our drawn conclusions in Section 3.6.
@@
   equilibrated based on when the distance between pores stops changing.
-%MRS: how did you determine when it stopped changing?  What statistical tests? By eye?
+  We determined when the distances stopped changing by applying the statistical
+  test, \texttt{pymbar.timeseries.detectEquilibration}, to the time series. 
+  Simulations of 400 ns give at least 50 ns of equilibrated simulation trajectory.
+  %BJC2: Do I cite the github repository for pymbar?
 
@@
   The colorbars on all diffraction patterns are normalized relative to
-  R-alkanes. We calculated the average intensity within R-alkanes of the
-  experimental pattern, $I_{avg}$.  We exclude intensities within $\pm$
-  30\degree~of the $q_r=0$ axis, since the simulated patterns differ from
-%MRS3: provide a little more information: because we think that the alkane-alkane density, averaged over angles, is the feature most likely to be replicated between experiment and simulation, rather than something like the peaks,  We have to leave out the very top and bottom because simulation places the Pi-stacking reflection in the middle of the alkane band.
-  experiment in those regions (See Fig. \ref{fig:XRDsim}).  We multiplied $I_{avg}$
-  by a scaling factor of 2.5.  
-  %MRS3: why 2.5? To match what? Need to explain.
-Intensities that appear in the experimental
-  pattern $\geq$ 2.5$*I_{avg}$ receive colorbar values of 1. The result of this
-  colorbar scaling method is shown in Figure \ref{fig:WAXS}. We apply the same
-  scaling method to the simulated patterns.
+  R-alkanes. We believe that the alkane-alkane density, averaged over all angles,
+  is the feature most likely to be replicated between experiment and simulation.
+  Other features are dependent on system ordering which is likely to have some
+  dependence on initial configuration. We calculated the average intensity within
+  R-alkanes of the experimental pattern, $I_{avg}$.  We exclude intensities
+  within $\pm$ 30\degree~of the $q_r=0$ axis, since the simulated patterns differ
+  from experiment in those regions. In contrast to the experimental WAXS pattern,
+  R-$\pi$ appearing in simulated diffraction patterns intersects with R-alkanes
+  (See Fig. \ref{fig:XRDsim}). We multiplied $I_{avg}$ by a scaling factor of
+  2.5. Intensities that appear in the experimental pattern $\geq$ 2.5$*I_{avg}$
+  receive colorbar values of 1. We apply the same scaling method to the simulated
+  patterns. We carefully chose a scaling factor of 2.5 in order to (1) visibly
+  display all features in the experimental pattern and (2) to allow us to compare
+  the relative intensities of features between simulated and experimental
+  diffraction patterns.
 
@@
 
-%  \subsection{Determination of Nanoscopic Structural Details}
   \subsection{Determining the Spatial Configuration of Monomers}
@@
 %MRS3: maybe the ``R-spots'' signal, to get agreement in number for grammar. Check other instances.
-  R-spots, which appears in both simulated XRD patterns, is a result of
-  hexagonal alkane chain packing. Previously, the spots in the diffraction
+  The R-spots signal, which appears in both simulated XRD patterns, is a result
+  of hexagonal alkane chain packing. Previously, the spots in the diffraction
   pattern had been explained as the product of tilted alkane chains. We measured
   the tilt angle of the alkane chains and showed that our system equilibrates to
-  an average tilt angle close to zero degrees (Fig.~\ref{fig:tilt}). To understand the
-  origin of the spots, we determined which atoms gave rise to the feature. Since
-  R-spots is present as higher intensity spots within R-alkanes, it is likely
-  that the spots arise as a consequence of the tails. By removing all non-tail atoms from the
-  trajectory and simulating a diffraction pattern, we were able to isolate the
-  cause of the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay
-  nearly flat, we plotted the centroids of the tails and measured the angle
-  between each centroid and its nearest neighbors with respect to the plane of
-  the membrane. We see distinct peaks in the distribution of these angles 
-  (Figure~\ref{fig:tail_packing}).
+  an average tilt angle close to zero degrees (Fig.~\ref{fig:tilt}). To
+  understand the origin of the spots, we determined which atoms gave rise to the
+  feature. Since R-spots is present as higher intensity spots within R-alkanes,
+  it is likely that the spots arise as a consequence of the tails. By removing
+  all non-tail atoms from the trajectory and simulating a diffraction pattern, we
+  were able to isolate the cause of the spots to the tails
+  (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted the
+  centroids of the tails and measured the angle between each centroid and its
+  nearest neighbors with respect to the plane of the membrane. We see distinct
+  peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).
 
@@
         %Do you feel you understand this? I suppose it is because the top of the tails must be correlated with the aromatic ring by covalent bonding?
+        %BJC2: Yea, I think the refelction is correlated to the aromatic rings. The system shown is the sandwiched configuration. The intensity of "R-pi"
+        % in this pattern is lower than in the pattern generated by the full system. The aromatic rings appear to strengthen the reflection. 
+        % Also, the system is layered in the z-direction, as we show, so a reflection like that should appear. 
   \end{figure}
@@
 
-%MRS3: specify which ones are referred to by neither.
-  Neither assembly deviates from its initial head group arrangement. R-helix is still 
-  faintly visible in the parallel displaced configuration and is absent in the 
-  sandwiched simulated diffraction pattern. The spectroscopic signatures are unique to
-  the two different head group configurations.
+  The sandwiched and parallell displaced assemblies do not deviate from their
+  initial head group arrangement. R-helix is still faintly visible in the
+  parallel displaced configuration and is absent in the sandwiched simulated
+  diffraction pattern. The spectroscopic signatures are unique to the two
+  different head group configurations.
 
@@
 
-  In order to address (\ref{point:poredefinition}), we plotted the number of
+  In order to address (\ref{point:poredefinition}), we plotted the number
   densities of heavy atoms in the head group, carbon atoms in the tail region
@@
   In all cases, the space in the pore region is filled with sodium ions and
-  head groups. There is a clear partition between the hydrophobic and hydrophilic
-  regions. Alkane tails do not cross into the pore region. 
-%MRS3: this is a bit weird, since you carry out the water experiments in this study, so you don't have to expect anything.
-MAybe something like: We address later in the paper where water might partition in the pores''.
-We expect that when 
-  water is introduced to the system, water molecules will occupy the hydrophilic region
-  and open up the pores for aqueous solute transport.
-
-%MRS3: maybe ``a more ordered pore structure''.  I wouldn't call any of them THAT ordered (it's really a judgement call), but the data certainly suggest sandwiched is more ordered than the others.
-  The sandwiched configuration (Fig. \ref{fig:layered_density}) shows a relatively
-  ordered pore structure. The number densities of components in all other
-  configurations are comparable. In contrast, sodium ions and head groups in the
-  sandwiched configuration are highly concentrated away from the pore center
-  meaning that there is vacancy in the pore region. 
-%MRS3: weaken this conclusion, since we don't know for sure: ``less likely to be stable''. Don't need to qualify ``in a real system'', since the same destabilization effects will occur in both.
-A vacant pore is very likely
-  to be unstable in a real system, further supporting the physical realism of the
-  parallel displaced configuration.
-
-  % BJC: TODO: Increase font size
-  %            Put insets in the figures that make it clear what configuration each represents
+  head groups. When systems are spaced 3.7 \AA~apart, there is less density in
+  the center of the pore indicating a more ordered pore structure. In both the
+  sandwich and parallel displaced configurations, we see the density of head
+  groups and sodium ions fall to less than 50 \% of its maximum at r = 0
+  (Fig.~\ref{fig:layered_density}).  The situation is most pronounced in the
+  sandwiched configuration where the maximum head group density occurs 0.44 nm from the pore
+  center. The parallel displaced configuration reaches its maximum 0.35 nm from
+  the pore center. In contrast, both system built with layers initially spaced
+  5 \AA~apart show verly little difference in density from its maximum. This 
+  implies a more uniform distribution of head groups within the pore center. 
+  % High vacancy is less likely to be stable in the real system
+
+  There is a partition between the hydrophobic and hydrophilic regions, however
+  it is a gradient in composition, rather than an abrupt division. Sodium ions
+  and head groups are not confined to just within the pore region. In all cases,
+  19 \% of sodium ions exist outside the pore region whose radius is assumed to
+  be 0.6 nm for this calculation (except sandwiched, 3.7 \AA~ initial layer
+  spacing, where 16 \% are outside the pore). Additionally, we see that in all
+  cases, about 3 \% of the plotted tail density is located within the pore region
+  (except sandwiched, 3.7 \AA~initial layer spacing, where 1.5 \% are within the
+  pore region). These observations bring into question how one should define a
+  pore in these types of systems. One usually measures a membrane's pore radius
+  based on the size of a molecule it can reject, however it is not clear where
+  the edges of the pores are and what size molecule would fit through. We leave
+  these investigations for a future study.
+
   \begin{figure}
@@
         \includegraphics[width=1\linewidth]{offset_density.png}
-        \caption{}
+        \caption{Parallel displaced, 3.7 \AA~initial layer spacing}
         \label{fig:offset_density}
@@
         \includegraphics[width=1\linewidth]{layered_density.png}
-        \caption{}
+        \caption{Sandwiched, 3.7 \AA~initial layer spacing}
         \label{fig:layered_density}
@@
         \includegraphics[width=1\linewidth]{disordered_offset_density.png}
-        \caption{}
+        \caption{Parallel displaced, 5 \AA~initial layer spacing}
         \label{fig:disordered_offset_density}
@@
         \includegraphics[width=1\linewidth]{disordered_density.png}
-        \caption{}
+        \caption{Sandwiched, 5 \AA~initial layer spacing}
         \label{fig:disorder_layered_density}
   \end{subfigure}
-%MRS3: I think it's a little more interesting, in that the pores clearly have hydrophobic and hydrophilic regions, but there is no abrupt transition.
-From 0.75 to 1.0 A, you have appreciable amounts of both moieties.
-And there isn't that much completely open sace.
-Sandwiched is a little more open.
-But if you look at the number density from 0.00 to 0.25, it's about the same, it just has less sodium in the tails.
-Interesting that the tail density is about the same for all of them.
-%MRS3: conclusions might be strenghtened if you could put in numbers (like integrated densitys (rememver 4pir^2 factor) of diffferet peaks in different regions.
-  \caption{In all cases, assemblies stay partitioned into hydrophilic and
-	  hydrophobic regions. The parallel displaced (a), the disordered parallel
-	  displaced (c), and the disordered sandwiched (d) show similar pore structures.
-	  The sandwiched configuration (b) exhibits an open pore structure with sodium
-	  ions and head groups concentrated away from the pore
-	  center.}~\label{fig:densities}
+  \caption{In all cases, the component radial distribution functions exhibit a
+	  composition gradient transitioning from the hydrophilic to the hydrophobic
+	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
+	  displaced (a), and sandwiched (b) configurations both show the highest
+	  concentrations of ions and head groups away from the pore center. Systems with
+	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
+	  concentrations of ions and head groups near the pore center, implying a more
+	  uniform, disordered pore.  }~\label{fig:densities}
   \end{figure}
@@
 
-  % BJC: Is it necessary to show layered configurations at this point?
-%MRS3: necessary for what point?
-%MRS3: remind peple what the structural points are, they don't want to go back.
-  We answered (\ref{point:water}) and further support (\ref{point:orientation})
+  We explored the affect of water on pore structure, addressing \ref{point:water}
+%  We answered (\ref{point:water}) and further support (\ref{point:orientation})
   by preparing parallel displaced and sandwiched configurations according to the
@@
   In systems built with 5 wt~\% water, the pore region becomes filled with
-  water. We plotted the number density of components in this system and see that
-  the pores become a soup of water molecules and sodium ions (Fig.
-  \ref{fig:water_density}). This system is a closer representation of the
-  H\textsubscript{II} phase which is typically synthesized with ca. 8 wt \%
-  water. 
-%MRS3: This next sentence is a little strange, since obviously we think it will be valuable from the introdiction; isn't really supporting data for this paragraph.
-We know that there are some selectivity features already.
-Maybe something like ``further analysis of water in these pores can help unravel the mechanisms for selective transport in separations of aqueous solutions?''.
-We believe that the hydrated membrane pores will be valuable for aqueous
-  separations. Further analysis of and transport within the H\textsubscript{II}
-  phase are left for future studies.
+  water. We plotted the number density of components in this system. As with the 
+  dry systems, we see a gradual compositional transition from hydrophilic to hydrophobic.  
+  We see that the pores become a soup of water molecules and sodium ions (Fig.
+  \ref{fig:water_density}).
+
+  The membrane swells when water is introduced. The location of maximum head
+  group density shifts from 0.35 to 0.62 nm and from 0.44 to 0.61 nm in the
+  parallel displaced and sandwiched configurations respectively.  We observe the
+  existence of ions, head groups and water outside the pore region. In the
+  hydrated system, the head groups drift beyond 1.5 \AA~from the pore center. In
+  the dry systems, head groups did not wander beyond 1.4 \AA~from the pore
+  center. Both observations suggest that all components are pushed radially
+  outward from the pore center, characteristic of a swelling process.
+
+  This system is a closer representation of the H\textsubscript{II} phase which
+  is typically synthesized with ca. 8 wt \% water. Further investigation of
+  hydrated systems can help unravel the mechanisms for selective transport in
+  separations of aqueous solutions.
 
@@
         \includegraphics[width=1\linewidth]{offset_solvated_density.png}
-        \caption{}
+        \caption{Parallel Displaced}
         \label{fig:offset_solvated_density}
@@
         \includegraphics[width=1\linewidth]{layered_solvated_density.png}
-        \caption{}
-        \label{fig:layered__solvated_density}
+        \caption{Sandwiched}
+        \label{fig:layered_solvated_density}
   \end{subfigure}
   \caption{Water fills the membrane pores in the parallel displaced (a) and 
-  sandwiched (b) configurations. Sodium ions are distributed more uniformly 
-%MRS3: more uniformly compared to what? parallel displaced, or previous sandwiched simulations?
-  in the sandwiched configuration.}
+  sandwiched (b) configurations. Sodium ions are distributed fairly uniformly
+  within the pore region, defined by a radius of 0.6 nm.}
   \label{fig:water_density}
@@
   than that of a nearly aligned film referenced here. We hypothesize that a thin,
-
-  perfectly aligned film would have a value of ionic conductivity in 
-%MRS3: changed:
-%close 
-closer
+  perfectly aligned film would have a value of ionic conductivity in closer
   agreement with our model.
@@
   \end{subfigure}
-  \caption{(a) Reflections produced by the crosslinked configuration fade relative
-  to the uncrosslinked system. The colorbar shown is the same used for the uncrosslinked
-  system. (b) The ionic conductivity is smaller relative to the uncrosslinked system, but
-  still much larger than the experimental value. (c) The distance between layers increases
-  when the system is crosslinked. (d) The pore spacing decreases when the membrane is 
-  crosslinked.}~\label{fig:xlink}
+  \caption{(a) Reflections produced by the crosslinked configuration fade
+	  relative to the uncrosslinked system. The colorbar shown is the same used for
+	  the uncrosslinked system. (b) The ionic conductivity is smaller relative to the
+	  uncrosslinked system, but still much larger than the experimental value. (c)
+	  The distance between layers increases when the system is crosslinked. (d) The
+	  pore spacing decreases when the membrane is crosslinked.}~\label{fig:xlink}
   \end{figure}
@@
 
-%MRS3: spend a bit more time explaining the findings to remind people what they are in a bit more detail.  Separate paragraph for each main finding.
-  % add stuff about pore structure and 'disordered' basin once there are concrete results 
   We have used a detailed molecular model of the Col\textsubscript{h} phase
@@
   to examine their structure with the same level of detail presented here.
-  Evidence strongly supports that monomers stay partitioned into layers and that
-  each layer contains 5 monomers. We have explored the affect of two different
-  $\pi$-$\pi$ stacking modes on the equilibrated membrane structure. Simulated
-  diffraction patterns generated from MD trajectories suggest that the
-  parallel-displaced configuration produces a structure with the closest match to
-  experiment. Finally, water is not needed to create well-defined pore
-  structures.
-
-%MRS3: this is a little informal. Something like ``With the structural understanding gained by these simulations'' 
-  Now that we have a good idea of what the membrane structure should
-  look like, we will evaluate transport of various solutes within the system. We
-  will apply the knowledge gained from this study in order to suggest
-  improvements to the existing system as well as to evaluate new unsynthesized
-  LLC systems.
+
+  Evidence strongly supports that monomers stay partitioned into layers which
+  stack to create pores and that each layer contains 5 monomers. We see periodic
+  spacing of layers based on the z-direction correlation function, $g(z)$ of
+  atoms in the tails and separately of atoms in the head groups.  Systems not
+  built with 5 monomers per layer result in assemblies whose pore-to-pore spacing
+  is inconsistent with experiment.
+
+  We have explored the affect of two different $\pi$-$\pi$ stacking modes on
+  the equilibrated membrane structure. Simulated diffraction patterns generated
+  from MD trajectories suggest that the parallel-displaced configuration produces
+  a structure with the closest match to experiment.
+
+  We have observed a number of metastable configurations. We witnessed
+  long-term stability of systems built with a varied number of monomers per layer
+  as well as in different $\pi$-$\pi$ stacking configurations. We also examined
+  how the structure changes based on the initial distance between layers and
+  showed how systems differ when built with layers spaced 5~\AA~ versus
+  3.7~\AA~apart. The configuration that showed the greatest agreement with
+  experiment was built in the parallel-displaced configuration, with 5 monomers
+  per layer and an initial layer spacing of 3.7 \AA.
+
+  We characterized the environment centered around the membrane pores and
+  learned that the pores are generally filled by monomer head groups and sodium
+  ions. Membranes prepared in the sandwiched configuration have more vacant
+  pores. We also observed that there is not a hard partition between hydrophlic
+  and hydrophilic regions, rather there is a gradient.  This finding has raised
+  questions about the nature of any size-exclusion separations.
+
+  We learned that water is not needed to create well-defined pore structures.
+  Systems whose pores were filled with varying amounts of water showed a decrease
+  in structuring relative to dry systems.
+
+  We justified that our system can reasonably estimate ionic conductivity.  Our
+  calculations are about 1 order of magnitude higher than experiment, however
+  that is to be expected since we are simulating a perfectly straight and
+  defect-free membrane.
+
+  Finally, we verified that our conclusions do not change when the system is
+  crosslinked by the algorithm we implemented. The diffraction pattern weakens
+  relative to the uncrosslinked system, the ionic conductivity drops by a factor
+  of ca. 1.5, in closer agreement with experiment, the pore spacing decreases and
+  the membrane becomes thicker.
+
+  With the structural understanding gained by these simulations, we will
+  evaluate transport of various solutes within the system. We will apply the
+  knowledge gained from this study in order to suggest improvements to the
+  existing system as well as to evaluate new unsynthesized LLC systems.
 

### 2017-12-19 Ben_Manuscripts/structure_paper/supplemental.tex
revisions

@@
 
-n{itemize}
-                %MRS2: make clear sampling what?
-                \item We are interested in 5 pore-to-pore distances which should all be equal in
-                a perfect hexagonal array, however only 4 distances are independent % can visualize this in supplemental material. Will make a lot of things more clear below.
-                \item Each pore spacing has its own trajectory of spacing vs. time. Using data collected after
-                the system is equilibrated, we calculate how long it takes for the data in each of the 5
-                trajetories to become uncorrelated using pymbar.timeseries.integratedAutocorrelationTime() % reference
+  \begin{figure}
+	\centering
+        \includegraphics[width=0.9\textwidth]{monomer.png}
+	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
+		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
+		the blue atom is sodium.}\label{fig:monomer}
+  \end{figure}
+
+  \begin{figure}
+	\centering
+        \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
+	\caption{The groups used for $g(z)$ calculations. Red atoms are in the
+		tails group. Green atoms are in the head group region. The blue atom is sodium. 
+		}\label{fig:monomer_color_coded}
+  \end{figure}
+
+  \begin{itemize}
+  \item We are interested in 5 pore-to-pore distances which should all be equal
+  in a perfect hexagonal array, however only 4 distances are independent % can
+  visualize this in supplemental material. Will make a lot of things more clear
+  below.
+  \item Each pore spacing has its own trajectory of spacing vs. time. Using
+  data collected after the system is equilibrated, we calculate how long it takes
+  for the data in each of the 5 trajetories to become uncorrelated using
+  pymbar.timeseries.integratedAutocorrelationTime() % reference
   \item We break the full trajectories down into sub-trajectories based on the
   maximum autocorrelation time of those found in the previous step.
-                \item For each bootstrap trial, we recreate an equilibrium trajectory by randomly
-                sampling pore spacings from the sub-trajectories
-                \item We get an average value for each pore spacing by finding the mean of the bootstrapped data
-                \item We calculate the overall average as the mean of all bootstrapped pore spacings
-                  %MRS3: this sounds a little convoluted below.  Should just be the standard error in the boostrap estimates of the pore spacing?
-                  %MRS3: this can be fixed in the draft not outline.
-                \item The uncertainty for each pore spacing is calculated as $\dfrac{<x> - x}{4}$ where $<x>$ is the
-                average spacing from the bootstrap trial and $x$ is the average value of one of the pore spacings.
+  \item For each bootstrap trial, we recreate an equilibrium trajectory by
+  randomly sampling pore spacings from the sub-trajectories 
+  \item We get an average value for each pore spacing by finding the mean of
+  the bootstrapped data
+  \item We calculate the overall average as the mean of all bootstrapped pore
+  spacings
+  \item The uncertainty for each pore spacing is calculated as $\dfrac{<x> -
+  x}{4}$ where $<x>$ is the average spacing from the bootstrap trial and $x$ is
+  the average value of one of the pore spacings.
   \item We report the mean of these uncertainties
-                % MRS: need to deal with the fact only 4 are independent in the bootstrapping?  How did we do that?
-                % BJC: Updated
   \end{itemize}
 
-\begin{wrapfigure}{R}{0.4\textwidth}
+  \begin{figure}
 	\centering
-      \includegraphics[width=0.4\textwidth]{tilt.png}
-      \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}     
-\end{wrapfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_layered_4.png}
+                \caption{4 mon/layer, Sandwiched}\label{fig:zdf_layered_4}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_offset_4.png}
+                \caption{4 mon/layer, Parallel Displaced}\label{fig:zdf_layered_4}
+        \end{subfigure}
+	\begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_layered_6.png}
+                \caption{6 mon/layer, Sandwiched}\label{fig:zdf_layered_6}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_offset_6.png}
+                \caption{6 mon/layer, Parallel Displaced}\label{fig:zdf_layered_6}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_layered_7.png}
+                \caption{7 mon/layer, Sandwiched}\label{fig:zdf_layered_7}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_offset_7.png}
+                \caption{7 mon/layer, Parallel Displaced}\label{fig:zdf_layered_7}
+        \end{subfigure}
+	\begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_layered_8.png}
+                \caption{8 mon/layer, Sandwiched}\label{fig:zdf_layered_8}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_offset_8.png}
+                \caption{8 mon/layer, Parallel Displaced}\label{fig:zdf_layered_8}
+        \end{subfigure}
+	\caption{$g(z)$ for all other configurations built with layers stacked 3.7 \AA~apart}\label{fig:zdf}
+  \end{figure}
+
+  \begin{figure}
+	\centering
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{rzplot_layered_4.png}
+                \caption{4 mon/layer, Sandwiched}\label{fig:rzplot_layered_4}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{rzplot_offset_4.png}
+                \caption{4 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_4}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{rzplot_layered_6.png}
+                \caption{6 mon/layer, Sandwiched}\label{fig:rzplot_layered_6}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{rzplot_offset_6.png}
+                \caption{6 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_6}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{rzplot_layered_7.png}
+                \caption{7 mon/layer, Sandwiched}\label{fig:rzplot_layered_7}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{rzplot_offset_7.png}
+                \caption{7 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_7}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{rzplot_layered_8.png}
+                \caption{8 mon/layer, Sandwiched}\label{fig:rzplot_layered_8}
+        \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{rzplot_offset_8.png}
+                \caption{8 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_8}
+        \end{subfigure}
+	\caption{Simulated XRD patterns for all other configurations built with
+		 layers stacked 3.7 \AA~apart}\label{fig:XRDsim}
+  \end{figure}
+
+%  \begin{wrapfigure}{R}{0.4\textwidth}
+%      \centering
+%      \includegraphics[width=0.4\textwidth]{tilt.png}
+%      \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}     
+%  \end{wrapfigure}
+
+%  \begin{figure}
+%	\centering
+%	\begin{subfigure}{0.45\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{ps5layered.png}
+%		\caption{}\label(fig:ps5layered}
+%	\end{subfigure}
+%	\begin{subfigure}
+%		\centering
+%		\includegraphics[width=\textwidth]{ps5offset.png}
+%		\caption{}\label{fig:ps5offset}
+%	\end{subfigure}
+%  \end{figure}
+
+  \begin{figure}[!ht]
+        \centering
+%        \begin{subfigure}{0.45\textwidth}
+%                \centering
+%                \hspace{-1cm}
+%                \vspace{1cm}
+%                \includegraphics[width=\textwidth,scale=2]{tails_topview.png}
+%                \caption{}\label{fig:tails_topview}
+%        \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{tails_rzplot.png}
+%                \caption{}\label{fig:tails_rzplot}
+%        \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+                \includegraphics[width=0.5\textwidth]{centroids_box.png}
+		\caption{Monomer tails pack together hexagonally. The centroid
+			of each tail is visualized as a blue sphere. The centroids are calculated based
+			on the red atoms in Figure~\ref{fig:monomer_color_coded}. The red sphere
+			highlights an example of an alkane tail centroid with its nearest neighbors
+			(green spheres) surrounding it in a hexagonal pattern.}\label{fig:centroids}
+%        \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{angles_traj_layered.png}
+%                \caption{}\label{fig:angle_distribution}
+%        \end{subfigure}
+%        \caption{(a) The trajectory can be stripped of all atoms except carbon
+%        atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
+%        still gives rise to R-spots. (c) Finding the center of mass and visualizing
+%        their coordinates reveals the hexagonal-like packing of the tails. (d) The
+%        distribution created by measuring the angle between each centroid (e.g. red
+%        in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
+%        plane has distinct spikes near 30\degree, which is consistent with the location
+%        of R-spots}\label{fig:tail_packing}
+  \end{figure}
 
@@
         \begin{subfigure}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{ps5layered.png}
-		\caption{}\label(fig:ps5layered}
-	\end{subfigure}
-	\begin{subfigure}
-		\centering
-		\includegraphics[width=\textwidth]{ps5offset.png}
-		\caption{}\label{fig:ps5offset}
-	\end{subfigure}
-\end{figure}
-
-\begin{figure}[!ht]
-        \centering
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \hspace{-1cm}
-                \vspace{1cm}
-                \includegraphics[width=\textwidth,scale=2]{tails_topview.png}
-                \caption{}\label{fig:tails_topview}
+                \includegraphics[width=\textwidth]{water_filled_pore.png}
+                \caption{}\label{fig:water_filled_pores}
         \end{subfigure}
         \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{tails_rzplot.png}
-                \caption{}\label{fig:tails_rzplot}
+                \includegraphics[width=\textwidth]{water_removed.png}
+                \caption{}\label{fig:water_removed}
         \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{centroids_box.png}
-                \caption{}\label{fig:centroids}
-        \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{angles_traj_layered.png}
-                \caption{}\label{fig:angle_distribution}
-        \end{subfigure}
-        \caption{(a) The trajectory can be stripped of all atoms except carbon
-        atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
-        still gives rise to R-spots. (c) Finding the center of mass and visualizing
-        their coordinates reveals the hexagonal-like packing of the tails. (d) The
-        distribution created by measuring the angle between each centroid (e.g. red
-        in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
-        plane has distinct spikes near 30\degree, which is consistent with the location
-        of R-spots}\label{fig:tail_packing}
+  \caption{(a) Pores built in the parallel displaced configuration with 5
+	  monomers per layer are filled with 5 wt\% water. (b) The same system is
+	  visualized with water molecules and sodium ions removed. Head groups vacate the
+	  pore region leaving an aqeuous solution of water and sodium ions.}\label{fig:water_pores}
   \end{figure}

### 2017-12-19 HII/Scripts/Poly_fit.py

@@ -19,6 +19,7 @@ import math
 # x = [1.01, 1.27, 1.85, 2.38, 2.83, 3.13, 3.96, 4.91]
 # y = [0.00, 0.19, 0.58, 0.96, 1.26, 1.47, 2.07, 2.75]
 
+
 def z_matrix(degree, t):
     Z = np.zeros((len(t), degree + 1))
     for i in range(0, degree + 1):

### 2017-12-19 HII/Scripts/Structure_char.py

@@ -280,7 +280,7 @@ def p2p_stats(p2ps, exclude, nboot, equil):
     return ensemble_avg, p2p_std, t
 
 
-def compdensity(component, pore_centers, start, box, cut=2, pores=4, nbins=50, rmax=3.5, buffer=0.0):
+def compdensity(component, pore_centers, start, box, cut=1.5, pores=4, nbins=50, rmax=3.5, buffer=0.0):
 
     """
     :param component: the coordinates of the component(s) which you want a radial distribution of at each frame
@@ -303,7 +303,7 @@ def compdensity(component, pore_centers, start, box, cut=2, pores=4, nbins=50, r
     n_ppore = tot_atoms // pores  # the total number of components in each pore
 
     nT = component.shape[0]
-
+    zbox = np.mean(box[:, 2, 2])
     # Find the approximate max and minimum z values of the components based on the last frame
 
     zmax = np.max(component[-1, :, 2])
@@ -323,7 +323,7 @@ def compdensity(component, pore_centers, start, box, cut=2, pores=4, nbins=50, r
     #                 dist = np.linalg.norm(component[k, i * n_ppore + j, :2] - pore_centers[:, i, k])
     #                 dist_from_center.append(dist)
 
-    density = np.zeros([nbins])
+    density = np.zeros([nbins])  # number / nm^3
     for t in tqdm.tqdm(range(start, nT)):
         for p in range(pores):
             # narrow down the positions to those that are with 'cut' of at least one pore
@@ -337,15 +337,17 @@ def compdensity(component, pore_centers, start, box, cut=2, pores=4, nbins=50, r
             hist, bin_edges = np.histogram(d_sorted[:stop], bins=nbins, range=(0, cut))  # the range option is necessary
             #  to make sure we have equal sized bins on every iteration
 
-            density += hist / box[t, 2, 2]
+            density += hist
 
-    density /= (tot_atoms*pores*(nT - start))  # take average
-    bin_width = cut / (nbins)
+    density /= zbox*(nT - start)  # take average
+    bin_width = cut / nbins
 
     # normalize based on area of anulus where bin is located
     r = np.zeros([nbins])
+    normalization = []
     for i in range(nbins):
-        density[i] /= np.pi*(bin_edges[i+1] - bin_edges[i])**2
+        normalization.append(np.pi*(bin_edges[i+1]**2 - bin_edges[i]**2))
[…]

### 2017-12-19 llclib/transform.py

@@ -285,6 +285,15 @@ def shift_matrices(images, angle, xbox, ybox):
 
 
 def pbcs(pts, images, angle, box, frame, nogap=False):
+    """
+    :param pts:
+    :param images:
+    :param angle:
+    :param box:
+    :param frame:
+    :param nogap:
+    :return:
+    """
 
     xbox = np.linalg.norm(box[0, 0, :])
     ybox = np.linalg.norm(box[0, 1, :])

### 2017-12-19 Ben_Manuscripts/structure_paper/Draft.tex
updated draft with comments.

@@
 \usepackage{setspace}
+\usepackage{color}
 \doublespacing
@@
   species, while maintaining the same retention of an undesired species.
+
+  %MRS4: are all commercial RO membranes just like this? This seems
+  %awfully specific.  
+  %MRS4: these two paragraphs are perhaps not
+  %ideal.  They describe the process of making the membranes, but that
+  %is not what we need as the introduction to THIS paper.  Instead, you
+  %need to focus on the strength/issues with RO and NF that motivate this research.
 
@@
 It should be an introduction to what you will talk about in the paper, not to everything related.
- % Improved RO membranes can make desalination more sustainable. Only 0.5 \% of
+ % Improved RO membranes can make desalination more sustainable. Only 0.5\% of
  % the world's water is fresh. Desalination is an important source of potable
@@
   The permeability-selectivity tradeoff has the potential to be overcome by
-  designing membranes at the molecular level. Next-geneartion nanostructured
+  designing membranes at the molecular level. Next-generation nanostructured
   membranes with high selectivity permitted by a precisely controlled pore size
@@
   Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-  phase (Fig.\ref{fig:assembly}). The presence of ca. 10 wt \% water results in the
+  phase (Fig.\ref{fig:assembly}). The presence of ca. 10\% wt water results in the
   H\textsubscript{II} phase. In both cases, monomers assemble into mesophases
@@
   groups oriented inward towards the cylinder center.  The hydrophilic region can
-  act as a pore for aqueous separations.  One can envision tailoring the pore
+  act as a pore for aqueous separations. 
+  %MRS4: aren't' there some citations where Gin and noble at least try to separate things (Even at low efficiency) to determine the size?
+(zhou_supported_2005) that should be cited here on ``act as a pore'' to show these are at least existing (if not usable
+ One can envision tailoring the pore
   region for specific separations by changing the monomer chemistry.
+%MRS4: can cite the Resel paper paper when changed tails and got different pore-to-pore distances as an example of changing monomer chemistry.
 
@@
   macroscopically aligned, resulting in low flux membranes, and no clear route
-  towards scalable and economical filtration. In 2014, Feng et al. showed that
+  towards scalable and economical filtration. In 2014, Feng et al.~showed that
   the mesophases could be aligned using a magnetic field with subsequent
   crosslinking to lock the structure in place \cite{feng_scalable_2014}. In 2016,
-  Feng et al. showed that the same result could be obtained using a technique
+  Feng et al.~showed that the same result could be obtained using a technique
   termed soft confinement \cite{feng_thin_2016}.
@@
   Na-GA3C11 with some characterization done after minor structural modifications.
-  Resel et al. varied the length of the monomer tails and the counterion used and
-  observed its affect on pore spacing \cite{resel_structural_2000}.  Their study
-  offers no insight into dynamics within the pore. In a later study of rejection
+  Resel et al.~varied the length of the monomer tails and the counterion used and
+  observed its affect on pore spacing \cite{resel_structural_2000}.
+
+%MRS4: is this sentence needed here? was there an expectation it would? 
+%Their study offers no insight into dynamics within the pore. 
+In a later study of rejection
   performance, it was shown that membranes formed by Na-GA3C11 cannot perform
@@
   from molecular dynamics simulations will provide the required level of detail
-  (Fig. \ref{fig:detail}).  We can directly observe solute transport and suggest
+  (Fig. \ref{fig:detail}),
+%MRS4: added as caveat.
+  assuming the force fields are sufficiently accurate.
+%MRS4: also added.
+  with such an atomistic model,
+  We can directly observe solute transport and suggest
   governing mechanisms. We can observe how the choice of head group may influence
@@
   (WAXS) patterns useful for reconstructing structural data.  
-
+  %MRS4: you should mention that the two phases appear to have similar pore-to-pore distances, 
+  %suggesting they are not very different.
+
+  %MRS4: weird to have a one sentence paragraph.  Maybe combine with next after rephrasing?
   Despite having structural data, there is still information which experiment
@@
   Monomers in the Col\textsubscript{h} system are theorized to be partitioned
-  into stacked layers which form columnar pores. We want to know
+  into stacked layers which form columnar pores. We %MRS4:want 
+  would like to know
 
@@
   A simple molecular simulation study of a similar molecule suggested that
-  there are 4 monomers in each layer. Their estimation is based on a simulated
+  there are 4 monomers in each layer.!\cite{zhu_methacrylated_2006}.  
+  %MRS4: moving citation to end of first reference of a paper. 
+%MRS4: rephrase:
+However, their estimate 
+is based on a simulated
   system containing only 16 total monomers which likely does not sufficiently
   model the chemical environment present in the real system
-  \cite{zhu_methacrylated_2006}.  A separate calculation based on the volume of
+
+A separate calculation based on the volume of
   the liquid crystal monomers proposes that there are seven monomers in each
   layer \cite{resel_structural_2000}.  A molecular model orders of magnitude
-  larger than any other reported atomistic liquid crystal membrane simulations
+  larger than any other reported atomistic liquid crystal membrane simulations,
+%MR4: added 
+as we present here,
   has the best chance of directly answering this question.  We will directly
@@
 
-  The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly
+  The $\pi$-$\pi$ stacking interactions may be a driving force of self-assembly
   in this system \cite{gazit_possible_2002}. Gas phase ab initio studies of
@@
   color turns from transparent to slightly opaque and a hexagonal phase forms.
-  Although we will not explore whether water is necessary for self assembly, we
+  Although we will not explore whether water is necessary for self-assembly, we
   hypothesize that the hydrogen bonding network formed by the water may play a
@@
 %BJC2: I will annotate it with the names R-pi, R-alkanes etc. Is that what you mean?
+%MRS4: that works fine.  We just need a way to connect what is in the figure with the names used in the text.  Ideally there would not be two sets of labels, just one. 
 	\caption{(a) The repeat spacing in the 1D small angle X-ray scattering pattern
@@
   \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-
+%MRS4: somewhere would need to specify things like time step tau_t, tau_p, etc., so that people could in theory replicate 
+the experiments.  Note: we should put scripts and starting configurations (not all that were done but the important ones) in a public repository by the time of submission.  
   An ensemble of characteristic, low-energy vacuum monomer configurations
@@
   reassigned using molcharge.
+%MRS4: I would give a ``plain text'' version of the script in supplementary.
 %MRS3: need to say what molcharge is.
@@
 %molcharge shipped with QUACPAC from ...". Is that not enough?
+%MRS4: sorry, missed that.  Maybe put software command names in \texttt{software} to make it clear what they are.
   Using the new charges, the monomer system was
@@
 
-  The timescale for self assembly of monomers into the hexagonal phase is
+%MRS4: check grammar additions in this paragraph.
+  The timescale for self-assembly of monomers into the hexagonal phase is
   unknown and likely outside of a reasonable length for an atomistic simulation,
   calling for a more efficient way to build the system.  Previous work has shown
-  a coarse grain model self assemble into the H\textsubscript{II} phase
-  configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.  We
+  a coarse-grained model self assemble into the H\textsubscript{II} phase
+  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
   attempted atomistic self-assembly by packing monomers into a box using Packmol
   \cite{martinez_packmol:_2009}.  Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system To bypass the slow
-  self-assembly process, python scripts are used to assemble monomers into a
+  indicators of progress towards an ordered system. To bypass the slow
+  self-assembly process, Python scripts are used to assemble monomers into a
   structure close to one of a number of hypothesized equilibrium configurations
@@
   pore's central axis, does not influence the equilibrium structure when a
-  reasonable value is chosen (See Supplemental). The pore radius is chosen to be
+  reasonable value is chosen (See Supplemental Information). The pore radius is chosen to be
   0.6 nm in our initial configurations because the pore size is estimated to be
-  $\approx$ 1.2 nm. The initial distance between pores also has little effect on
+  $\approx$ 1.2 nm.
+%MRS4: provide citation here for 1.2 number.
+ The initial distance between pores also has little effect on
   the the equilibrated structure. However, one should not start them too close or
   there will be high energy repulsions during early equilibration. We chose an
-  initial pore spacing of 4.5 nm, $\approx$ 10 \% larger than the experimental
+  initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental
   value of 4.12 nm.  The distance between layers, the rotation of the layers with
@@
   We explore two different initial layer spacings. The first is exactly equal to
-  R-$\pi$ with layers placed so aromatic rings are stacked 3.7 \angstrom~ apart
+  R-$\pi$ with layers placed so aromatic rings are stacked 3.7 \angstrom~apart
   in the z-direction. A second system is explored with an initial layer spacing
-  of 5 \angstrom. A third system with an initial layer spacing of 10 \angstrom was
+  of 5 \angstrom. A third system with an initial layer spacing of 10 \angstrom~was
+  %MRS4: this is probably OK here, but you do want to move away from describing things historically (the order in which the ideas were had and tested) and the logical ordering to communicate the story.
+You want to do the second whenever possible.
+Think about this going over the paper and try to shift from historical presentation of results to story-based ordering.
   briefly explored. When layers are spaced out too far, they will collapse
-  on each other while simultaneously slipping in between layers of adjacent pores
+  on each other while simultaneously slipping in between layers of adjacent pores,
   which leads to an artificially thick membrane with pores spaced closely
@@
   ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
-  The T-shaped configuration was ruled out because its $\approx$ 5 \angstrom~
+  The T-shaped configuration was ruled out because its $\sim$5 \angstrom~
   equilibrium stacking distance ~\cite{sinnokrot_estimates_2002} is inconsistent
@@
 
+%MRS4: describe what the points are, people don't want to go back and look.
   As outlined in (\ref{point:monomernum}) the number of monomers in each layer is
@@
   %BJC2: Do I cite the github repository for pymbar?
-
+  %MRS4, yes, though also http://pubs.acs.org.colorado.idm.oclc.org/doi/abs/10.1021/acs.jctc.5b00784
   To calculate the equilibrated pore spacing, we measured the distance between
@@
   % BJC: To be replaced by Joe's description
+  {\color{red}This section replaced by Yelk/Glaser text}. 
   Simulated X-ray diffraction patterns are generated based on atomic
@@
   within $\pm$ 30\degree~of the $q_r=0$ axis, since the simulated patterns differ
-  from experiment in those regions. In contrast to the experimental WAXS pattern,
+  from experiment in those regions. 
+%MRS4: added to connect.
+Specifically, in contrast to the experimental WAXS pattern,
   R-$\pi$ appearing in simulated diffraction patterns intersects with R-alkanes
   (See Fig. \ref{fig:XRDsim}). We multiplied $I_{avg}$ by a scaling factor of
-  2.5. Intensities that appear in the experimental pattern $\geq$ 2.5$*I_{avg}$
+  2.5. Intensities that appear in the experimental pattern $\geq$ 2.5$I_{avg}$
   receive colorbar values of 1. We apply the same scaling method to the simulated
@@
   % BJC: I think this figure belongs somewhere else 
+%MRS4: yeah, probably. Possibly supplemental information.
   \begin{figure}
@@
 		in each layer increases. The pore spacing of a system starting in the
-		sandwiched configuration is systematically lower than that started in an offset
+		sandwiched configuration is systematically 
+%MRS4: added
+slightly
+lower than that started in an offset
 		configuration. }~\label{fig:p2p}
@@
   chains. Using a Fourier transform of $g(z)$, we see that sandwiched
-  configuration layers stack 4.39 \angstrom~ apart while parallel displaced
-  configuration layers stack 4.38 \angstrom~ apart.
+  configuration layers stack 4.39 \angstrom~apart while parallel displaced
+  configuration layers stack 4.38 \angstrom~apart.
 
@@
   the parallel displaced aromatic rings. It is a subharmonic of R-$\pi$ since the
-  nearest vertically stacked head group to any given head group is 7.4 \AA~ away.
+  nearest vertically stacked head group to any given head group is 7.4 \AA~away.
 
@@
   forcefields. 
-%MRS3: cite specific efforts on treatement if pi-stacking.
+%MRS3: cite specific efforts on treatment if pi-stacking. 
+%MRS4: i.e. add citations.
 We could implement a polarizable force field, however it is likely
@@
         %Do you feel you understand this? I suppose it is because the top of the tails must be correlated with the aromatic ring by covalent bonding?
-        %BJC2: Yea, I think the refelction is correlated to the aromatic rings. The system shown is the sandwiched configuration. The intensity of "R-pi"
+        %BJC2: Yea, I think the reflection is correlated to the aromatic rings. The system shown is the sandwiched configuration. The intensity of "R-pi"
         % in this pattern is lower than in the pattern generated by the full system. The aromatic rings appear to strengthen the reflection. 
         % Also, the system is layered in the z-direction, as we show, so a reflection like that should appear. 
+        %MRS4: did you use a different scaling for the color bar here than above? If so, mention.
   \end{figure}
@@
 
+%MRS4: can we come up with another name?
+I still think disordered pores is a decent name, since there is no pi-stacking layering.
+``structures that form when layers are 5 AA apart'' is not so good.
+or ``more disordered''?
 %  The $z$-direction correlation functions show that layers in our model prefer
-%  to stack further apart than 3.7 \angstrom as suggested by experiment.
+%  to stack further apart than 3.7 \angstrom~as suggested by experiment.
   When systems are built with layers stacked 5.0 \AA~apart then
@@
 
-  The sandwiched and parallell displaced assemblies do not deviate from their
+  The sandwiched and parallel displaced assemblies do not deviate from their
   initial head group arrangement. R-helix is still faintly visible in the
@@
         \end{subfigure}
-	\caption{In comparison to systems built with 3.7 \AA~ initial layer spacing,  
+	\caption{In comparison to systems built with 3.7 \AA~initial layer spacing,  
                 the simulated X-ray diffraction patterns of the parallel displaced (a) and 
  		sandwiched (b) configurations are different when systems are built with 
- 		a 5 \AA~ initial layer spacing, most notably in the region bounded by R-alkanes.
+ 		a 5 \AA~initial layer spacing, most notably in the region bounded by R-alkanes.
       		When layers are stacked further apart, the distance between layers increases (c)
@@
   sandwich and parallel displaced configurations, we see the density of head
-  groups and sodium ions fall to less than 50 \% of its maximum at r = 0
+  groups and sodium ions fall to less than 50\% of its maximum at r = 0
   (Fig.~\ref{fig:layered_density}).  The situation is most pronounced in the
@@
   the pore center. In contrast, both system built with layers initially spaced
-  5 \AA~apart show verly little difference in density from its maximum. This 
+  5 \AA~apart show very little difference in density from its maximum. This 
   implies a more uniform distribution of head groups within the pore center. 
@@
   and head groups are not confined to just within the pore region. In all cases,
-  19 \% of sodium ions exist outside the pore region whose radius is assumed to
-  be 0.6 nm for this calculation (except sandwiched, 3.7 \AA~ initial layer
-  spacing, where 16 \% are outside the pore). Additionally, we see that in all
-  cases, about 3 \% of the plotted tail density is located within the pore region
-  (except sandwiched, 3.7 \AA~initial layer spacing, where 1.5 \% are within the
+  19\% of sodium ions exist outside the pore region whose radius is assumed to
+  be 0.6 nm for this calculation (except sandwiched, 3.7 \AA~initial layer
+  spacing, where 16\% are outside the pore). Additionally, we see that in all
+  cases, about 3\% of the plotted tail density is located within the pore region
+  (except sandwiched, 3.7 \AA~initial layer spacing, where 1.5\% are within the
   pore region). These observations bring into question how one should define a
@@
   from 0.5 to 5 percent. Our lower bound models a system with on average 2 water
-  molecules for each monomer layer. Figure ~\ref{fig:solvation} shows the
+  molecules for each monomer layer. Figure~\ref{fig:solvation} shows the
   simulated diffraction patterns resulting from each configuration.
@@
 
-  In all cases, water disrupts structuring of the model. The plots in Figure
-  ~\ref{fig:solvation} are normalized to have the same colorbar as the dry
-  systems. The intensity of the reflections decrease when water is added to the
-  system. In systems built with 5 wt \% water, R-$\pi$ and R-spots
+  In all cases, water disrupts structuring of the model. The plots in Figure~\ref{fig:solvation} 
+  are normalized to have the same colorbar as the dry
+  systems. 
+  %MRS4: not quite sure what it means to be normalized to have the same colorbar?
+  The intensity of the reflections decrease when water is added to the
+  system. In systems built with 5\% wt water, R-$\pi$ and R-spots
   become nearly indistinguishable from R-alkanes.
@@
   eliminate the possibility that water is necessary in order to drive
-  self-assembly, however, studying the mechanisms of self assembly is beyond the
+  self-assembly, but studying the mechanisms of self-assembly is beyond the
   scope of this work. According to our model, once the system has formed the
@@
 
-  In systems built with 5 wt~\% water, the pore region becomes filled with
+  In systems built with 5\% wt water, the pore region becomes filled with
   water. We plotted the number density of components in this system. As with the 
@@
   \ref{fig:water_density}). 
+  %MRS4: soup is too colloquial.
 
@@
   This system is a closer representation of the H\textsubscript{II} phase which
-  is typically synthesized with ca. 8 wt \% water. Further investigation of
+  is typically synthesized with ca. 8\% wt water. Further investigation of
   hydrated systems can help unravel the mechanisms for selective transport in
@@
   \end{figure}
-
+  %MRS4: weird there's a head group peak in the center. Not enough statistics, so shot noise from the r^2 dr weighting?
   \subsection{Model Ionic Conductivity Measurements}
@@
   the crosslinked system in the NPT ensemble for 100 ns. The distance between
-  pores shrinks by 0.4 \angstrom~ and the distance between layers increases by
-  0.04 \AA~ after the system is crosslinked. All major features are still present
+  pores shrinks by 0.4 \angstrom~and the distance between layers increases by
+  0.04 \AA~after the system is crosslinked. All major features are still present
   in the simulated XRD patterns, however at lower intensities
@@
   how the structure changes based on the initial distance between layers and
-  showed how systems differ when built with layers spaced 5~\AA~ versus
+  showed how systems differ when built with layers spaced 5~\AA~versus
   3.7~\AA~apart. The configuration that showed the greatest agreement with
@@
   per layer and an initial layer spacing of 3.7 \AA.  
+  %MRS4: do we have a sense of how consistent this behavior is?
+I.e.
+if started with 4 apart does it look like 3.7 or 5 separations?
+How about 4.5?
+Is there a gradual range of changes?
+Can we rule this out?
+What work was done on this?
 
@@
   learned that the pores are generally filled by monomer head groups and sodium
-  ions. Membranes prepared in the sandwiched configuration have more vacant
+  ions. Membranes prepared in the sandwiched configuration have more 
+  %MRS4: lower-density instead of vacant?
+  vacant
   pores. We also observed that there is not a hard partition between hydrophlic
@@
 % LocalWords:  KJ NVT kJ Parrinello Rahman gmx solvate polymerization FRP FRPs
-% LocalWords:  crosslink binned DC MSD subharmonic matplotlib GAFF's xrd llc
-% LocalWords:  polarizable reconcilable screenshot crosslinked uncrosslinked
+% LocalWords:  crosslink binned DC MSD subharmonic matplotlib GAFF's xrd llc ab
+% LocalWords:  polarizable reconcilable screenshot crosslinked uncrosslinked AA
+% LocalWords:  nanofiltration permeability interfacial diamine polysulfone der
+% LocalWords:  trimesoyl immiscible polymerizes etching Osuji's nanostructured
+% LocalWords:  Donnan modelling nanotubes monodispersity maruyama Zeolites Col
+% LocalWords:  lyotropic thermotropic png kinetically colorbar gromacs hess dr
+% LocalWords:  gimp disassociate pore's barostat racemic colorbars Nernst LLCs
+% LocalWords:  entropic rzplot transitioning spoel github pymbar Yelk Glaser

### 2017-12-19 Ben_Manuscripts/structure_paper/Draft.tex
Modifications based on comments

@@
   %awfully specific. 
-  %MRS4: these two paragraphs are perhaps not
-  %ideal.  They describe the process of making the membranes, but that
-  %is not what we need as the introduction to THIS paper.  Instead, you
-  %need to focus on the strength/issues with RO and NF that motivate this research.
+  %BJC3: Yea, pretty much all commercial membranes are TFC polyamide
+  % but I edited it to make it less specific.
+
+  %MRS4: these two paragraphs are perhaps not ideal.  They describe the process
+  %of making the membranes, but that is not what we need as the introduction to
+  %THIS paper.  Instead, you need to focus on the strength/issues with RO and
+  %NF that motivate this research.
+  % BJC3: The point I am trying to make is that the way the membranes are made 
+  % results in either low selectivity or low permeability. I could just state
+  % that, or give a little background on the processes to make the point more
+  % tangible
 
@@
   support layer and an active layer made of a polymer matrix formed by
-  interfacial polymerization of a diamine. During the membrane fabrication,
-  aqueous diamine solution is allowed to penetrate into the polysulfone support
-  layer which is then immersed in trimesoyl chloride, a compound that is
-  immiscible in water. Diamine polymerizes with trimesoyl chloride at the
-  solution interface and creates a thin film that physically adheres to the
-  polysulfone support. The polymer matrix is dense and highly crosslinked
-  which leads to low permeability.
-
-  NF membranes are typically made by a phase inversion process. During phase
-  inversion, a thin polymer film is precipitated out of a polymer solution.
-  Through the use of a non-solvent, a polymer-rich and polymer-poor phase is
-  formed. A membrane is created as the polymer-poor phase forms pores in the
-  polymer-rich phase. Resultant pores are polydisperse in size which hurts
-  membrane selectivity. A second technique used to create NF membranes is call
-  track etching in which a polymer film is bombarded with charged particles, then
-  chemically etched to create pores. The pores are uniform which benefits
-  selectivity, however the membrane has a low porosity and subsequent low
-  permeability.
+  interfacial polymerization. During synthesis, a step-growth polymerization
+  reaction occurs at the interface of an aqueous monomer solution, which has been
+  soaked into the support layer, and an organic solution of a second monomer. The
+  polymer matrix is dense and highly crosslinked which gives high rejections but
+  low permeability.
+
+  %During membrane fabrication,
+  %aqueous diamine solution is allowed to penetrate into the polysulfone support
+  %layer which is then immersed in trimesoyl chloride, a compound that is
+  %immiscible in water. Diamine polymerizes with trimesoyl chloride at the
+  %solution interface and creates a thin film that physically adheres to the
+  %polysulfone support.
+
+%  solution.  Through the use of a non-solvent, a polymer-rich and polymer-poor
+%  phase is formed. A membrane is created as the polymer-poor phase forms pores in
+%  the polymer-rich phase. 
+%  During phase inversion, a thin polymer film is precipitated out of a polymer
+  NF membranes are typically made by a phase inversion process. The most widely
+  used phase inversion process is immersion precipitation, during which a polymer
+  dissolved in a solvent is submerged in a non-solvent. A solid, porous membrane 
+  is all that remains once all solvent has been removed by non-solvent exchange. 
+  Resultant pores are polydisperse in size which hurts membrane selectivity.  A
+  second technique used to create NF membranes is call track etching in which a
+  polymer film is bombarded with charged particles, then chemically etched to
+  create pores. The pores are uniform which benefits selectivity, however the
+  membranes have a low porosity and subsequent low permeability.
 
@@
   production.  \cite{feng_scalable_2014} LLC systems created by the monomer
-  Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied experimentally.
+  Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied
+  experimentally.
   \cite{smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}
-  Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
-  phase (Fig.\ref{fig:assembly}). The presence of ca. 10\% wt water results in the
+  Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h} phase
+  (Fig.\ref{fig:assembly}). The presence of ca. 10\% wt water results in the
   H\textsubscript{II} phase. In both cases, monomers assemble into mesophases
@@
   groups oriented inward towards the cylinder center.  The hydrophilic region can
-  act as a pore for aqueous separations. 
-  %MRS4: aren't' there some citations where Gin and noble at least try to separate things (Even at low efficiency) to determine the size?
-(zhou_supported_2005) that should be cited here on ``act as a pore'' to show these are at least existing (if not usable
- One can envision tailoring the pore
-  region for specific separations by changing the monomer chemistry.
-%MRS4: can cite the Resel paper paper when changed tails and got different pore-to-pore distances as an example of changing monomer chemistry.
+  act as a pore for aqueous separations \cite{zhou_supported_2005}.  One can
+  envision tailoring the pore region for specific separations by changing the
+  monomer chemistry \cite{resel_h2-phase_2000}.
 
@@
   Resel et al.~varied the length of the monomer tails and the counterion used and
-  observed its affect on pore spacing \cite{resel_structural_2000}.
-
-%MRS4: is this sentence needed here? was there an expectation it would? 
-%Their study offers no insight into dynamics within the pore. 
-In a later study of rejection
-  performance, it was shown that membranes formed by Na-GA3C11 cannot perform
-  separations of solutes less than 1.2 nm in diameter because the pores are too
-  large \cite{zhou_supported_2005}.  We do not yet understand how to controllably
-  reduce the effective pore size or how to tune the chemical environment in the
-  nanopores for effective water desalination and small organic molecule
-  separations. The only source of predictive modeling for LLC systems have been
-  macroscopic models which likely do not adequately describe transport at these
-  length scales \cite{hatakeyama_water_2011}. It will be challenging to
+  observed its affect on pore spacing \cite{resel_structural_2000}.  In a later
+  study of rejection performance, it was shown that membranes formed by Na-GA3C11
+  cannot perform separations of solutes less than 1.2 nm in diameter because the
+  pores are too large \cite{zhou_supported_2005}.  We do not yet understand how
+  to controllably reduce the effective pore size or how to tune the chemical
+  environment in the nanopores for effective water desalination and small organic
+  molecule separations. The only source of predictive modeling for LLC systems
+  have been macroscopic models which likely do not adequately describe transport
+  at these length scales \cite{hatakeyama_water_2011}. It will be challenging to
   efficiently narrow down the large design space in a laboratory setting without
@@
 
-  %MRS3: this paragraph seems to be a little out of place: should go before a lot of the introductory material, since it lays out what you will be doing in the paper.
-  %BJC2: Paragraph moved up here from well below.
   In this study, we build a significantly more realistic atomistic model of LLC
@@
   from molecular dynamics simulations will provide the required level of detail
-  (Fig. \ref{fig:detail}),
-%MRS4: added as caveat.
-  assuming the force fields are sufficiently accurate.
-%MRS4: also added.
-  with such an atomistic model,
-  We can directly observe solute transport and suggest
-  governing mechanisms. We can observe how the choice of head group may influence
-  pore size for size exclusion driven separations. We can interchange counterions
-  which may influence both the pore size and the strength of the Donnan potential
-  which affects the degree to which the membrane can exclude charged species.
+  (Fig. \ref{fig:detail}), assuming the force fields are sufficiently accurate.
+  with such an atomistic model, We can directly observe solute transport and
+  suggest governing mechanisms. We can observe how the choice of head group may
+  influence pore size for size exclusion driven separations. We can interchange
+  counterions which may influence both the pore size and the strength of the
+  Donnan potential which affects the degree to which the membrane can exclude
+  charged species.
 
@@
   absence of water, and has detailed experimental wide-angle X-ray scattering
-  (WAXS) patterns useful for reconstructing structural data.  
-  %MRS4: you should mention that the two phases appear to have similar pore-to-pore distances, 
-  %suggesting they are not very different.
-
-  %MRS4: weird to have a one sentence paragraph.  Maybe combine with next after rephrasing?
+  (WAXS) patterns useful for reconstructing structural data. The two
+  phases appear to share similar structural characteristics since the pore 
+  spacings in each system are in close agreement \cite{resel_structural_2000,feng_thin_2016}.
+
   Despite having structural data, there is still information which experiment
-  cannot definitively answer. There are several key questions that we will
-  investigate.
-
-  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
-  into stacked layers which form columnar pores. We %MRS4:want 
-  would like to know
+  cannot definitively answer. Our current level of understanding suggests that
+  monomers partition into layers with head groups facing the center, then 
+  stack on top of each other to create pores that pack together hexagonally.
+  There are several key questions that we will investigate in order to
+  expand our understanding.
 
@@
   A simple molecular simulation study of a similar molecule suggested that
-  there are 4 monomers in each layer.!\cite{zhu_methacrylated_2006}.  
-  %MRS4: moving citation to end of first reference of a paper. 
-%MRS4: rephrase:
-However, their estimate 
-is based on a simulated
-  system containing only 16 total monomers which likely does not sufficiently
-  model the chemical environment present in the real system
-
-A separate calculation based on the volume of
-  the liquid crystal monomers proposes that there are seven monomers in each
-  layer \cite{resel_structural_2000}.  A molecular model orders of magnitude
-  larger than any other reported atomistic liquid crystal membrane simulations,
-%MR4: added 
-as we present here,
-  has the best chance of directly answering this question.  We will directly
-  change the layer composition and note its effect on membrane structure.
+  there are 4 monomers in each layer \cite{zhu_methacrylated_2006}. Their 
+  model likely does not sufficiently model the chemical environment present
+  in the real system since it only contains 16 total monomers.
+%BJC3: rephrased
+%  However, their estimate is based on a simulated system that contains 16 total
+%  monomers which likely does not sufficiently model the chemical environment
+%  present in the real system
+  A separate calculation based on the volume of the liquid crystal monomers
+  proposes that there are seven monomers in each layer
+  \cite{resel_structural_2000}.  A molecular model orders of magnitude larger
+  than any other reported atomistic liquid crystal membrane simulations, as we
+  present here, has the best chance of directly answering this question.  We will
+  directly change the layer composition and note its effect on membrane
+  structure.
 
@@
 %MRS4: that works fine.  We just need a way to connect what is in the figure with the names used in the text.  Ideally there would not be two sets of labels, just one.
+%BJC3: Got it, will do once I have more time to focus on figures 
 	\caption{(a) The repeat spacing in the 1D small angle X-ray scattering pattern
@@
   \cite{case_ambertools16_2016}. Atomic charges were assigned using the am1bccsym
-  method of molcharge shipped with QUACPAC from Openeye Scientific Software. All
-  molecular dynamics simulations were run using Gromacs 2016.
+  method of \texttt{molcharge} shipped with QUACPAC from Openeye Scientific
+  Software. All molecular dynamics simulations were run using Gromacs 2016.
   \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
+  the experiments.  An ensemble of characteristic, low-energy vacuum monomer
+  configurations were constructed by applying a simulated annealing process to a
+  parameterized monomer. Monomers were cooled from 1000K to 50K over 10
+  nanoseconds.  A low energy configuration was randomly pulled from the
+  trajectory and charges were reassigned using \texttt{molcharge}.  Using the new
+  charges, the monomer system was annealed again and a random monomer
+  configuration was pulled from the trajectory to be used for full system
+  construction (Figure~\ref{fig:python}a).  See supplemental information for
+  further detail.
+
+% Note: we should put scripts and starting configurations (not all that were
+% done but the important ones) in a public repository by the time of
+% submission. 
+%MRS4: I would give a ``plain text'' version of the script in supplementary. BJC: referring to parameterization script
 %MRS4: somewhere would need to specify things like time step tau_t, tau_p, etc., so that people could in theory replicate
-the experiments.  Note: we should put scripts and starting configurations (not all that were done but the important ones) in a public repository by the time of submission.  
-  An ensemble of characteristic, low-energy vacuum monomer configurations
-  were constructed by applying a simulated annealing process to a parameterized
-  monomer. Monomers were cooled from 1000K to 50K over 10 nanoseconds.  A low
-%MRS3: need to describe this in more detail, but can be in the supplementary. 
-%BJC2: would it be best to include the parameterization script
-  energy configuration was randomly pulled from the trajectory and charges were
-  reassigned using molcharge.
-%MRS4: I would give a ``plain text'' version of the script in supplementary.
-%MRS3: need to say what molcharge is.
-%BJC2: I say in paragraph above : "Atomic charges were assigned using the am1bccsym method of 
-%molcharge shipped with QUACPAC from ...". Is that not enough?
-%MRS4: sorry, missed that.  Maybe put software command names in \texttt{software} to make it clear what they are.
-  Using the new charges, the monomer system was
-  annealed again and a random monomer configuration was pulled from the
-  trajectory to be used for full system construction (Figure~\ref{fig:python}a).
-  See supplemental information for further detail.
 
@@
   pore's central axis, does not influence the equilibrium structure when a
-  reasonable value is chosen (See Supplemental Information). The pore radius is chosen to be
-  0.6 nm in our initial configurations because the pore size is estimated to be
-  $\approx$ 1.2 nm.
-%MRS4: provide citation here for 1.2 number.
- The initial distance between pores also has little effect on
-  the the equilibrated structure. However, one should not start them too close or
-  there will be high energy repulsions during early equilibration. We chose an
-  initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental
-  value of 4.12 nm.  The distance between layers, the rotation of the layers with
-  respect to adjacent layers, and the number of monomers per layer do influence
-  the equilibrium structure and require further justification for their choices.
-  We rely on experimental data to inform them.
+  reasonable value is chosen (See Supplemental Information). The pore radius is
+  chosen to be 0.6 nm in our initial configurations because the pore size is
+  estimated to be $\approx$ 1.2 nm \cite{zhou_supported_2005}.  The initial
+  distance between pores also has little effect on the the equilibrated
+  structure. However, one should not start them too close or there will be high
+  energy repulsions during early equilibration. We chose an initial pore spacing
+  of 4.5 nm, $\sim$10\% larger than the experimental value of 4.12 nm.  The
+  distance between layers, the rotation of the layers with respect to adjacent
+  layers, and the number of monomers per layer do influence the equilibrium
+  structure and require further justification for their choices.  We rely on
+  experimental data to inform them.
 
   We chose the layer spacing for the initial configuration based on R-$\pi$ and
-  then allowed the system to readjust during equilibration. Each monomer was rotated
-  so the plane of the aromatic head groups would be coplanar with the xy plane.
-  We explore two different initial layer spacings. The first is exactly equal to
-  R-$\pi$ with layers placed so aromatic rings are stacked 3.7 \angstrom~apart
-  in the z-direction. A second system is explored with an initial layer spacing
-  of 5 \angstrom. A third system with an initial layer spacing of 10 \angstrom~was
-  %MRS4: this is probably OK here, but you do want to move away from describing things historically (the order in which the ideas were had and tested) and the logical ordering to communicate the story.
-You want to do the second whenever possible.
-Think about this going over the paper and try to shift from historical presentation of results to story-based ordering.
-  briefly explored. When layers are spaced out too far, they will collapse
-  on each other while simultaneously slipping in between layers of adjacent pores,
-  which leads to an artificially thick membrane with pores spaced closely
-  together. 
-  Further details of simulations with large layer spacing are in the supplemental information.
-%There will be no further discussion of this system but the interested
-%  reader can learn more about it in the supplemental information.
+  then allowed the system to readjust during equilibration. Each monomer was
+  rotated so the plane of the aromatic head groups would be coplanar with the xy
+  plane.  We explore two different initial layer spacings. The first is exactly
+  equal to R-$\pi$ with layers placed so aromatic rings are stacked 3.7
+  \angstrom~apart in the z-direction. A second system is explored with an initial
+  layer spacing of 5 \angstrom. A third system with an initial layer spacing of
+  10 \angstrom~was briefly explored. When layers are spaced out too far, they
+  will collapse on each other while simultaneously slipping in between layers of
+  adjacent pores, which leads to an artificially thick membrane with pores spaced
+  closely together.  Further details of simulations with large layer spacing are
+  in the supplemental information.
 
@@
 
-%MRS4: describe what the points are, people don't want to go back and look.
-  As outlined in (\ref{point:monomernum}) the number of monomers in each layer is
-  unknown. We tested configurations constructed with a varied number of
-  monomers per layer. Systems were built in the offset and parallel displaced
-  configurations with 4, 5, 6, 7 and 8 monomers per layer.
+  The number of monomers in each layer is unknown, as state in
+  (\ref{point:monomernum}). We tested configurations constructed with a varied
+  number of monomers per layer. Systems were built in the offset and parallel
+  displaced configurations with 4, 5, 6, 7 and 8 monomers per layer.
 
@@
 
-  % BJC: Need to make it clear that this was not done on all systems
-
   In order to fully match synthetic procedures, we created a crosslinking
   algorithm that can be applied to equilibrated structures. The purpose of
-  crosslinking
-  is to maintain macroscopic alignment of the crystalline domains, 
+  crosslinking is to maintain macroscopic alignment of the crystalline domains,
   ensuring aligned, hexagonally packed pores. For that reason, we are not
@@
   addition could occur as dummy atoms. The crosslinking procedure is carried out
-  iteratively. During each iteration, bonding carbon atoms are chosen based on
-  a distance cut-off. The topology is updated with new bonds and dummy hydrogen
+  iteratively. During each iteration, bonding carbon atoms are chosen based on a
+  distance cut-off. The topology is updated with new bonds and dummy hydrogen
   atoms are changed to appropriate hydrogen types. Head-to-tail addition was the
   only propagation mode considered due to its dominance in the real system.
-%MRS3: citation why it dominates the real system.
-%BJC2: Yea. There are a few citations that I need to make. I know they exist
-% but I need to track them down. I've prioritized that last. 
   Direction of attack was not considered because the resultant mixture is
@@
   within $\pm$ 30\degree~of the $q_r=0$ axis, since the simulated patterns differ
-  from experiment in those regions. 
-%MRS4: added to connect.
-Specifically, in contrast to the experimental WAXS pattern,
-  R-$\pi$ appearing in simulated diffraction patterns intersects with R-alkanes
-  (See Fig. \ref{fig:XRDsim}). We multiplied $I_{avg}$ by a scaling factor of
-  2.5. Intensities that appear in the experimental pattern $\geq$ 2.5$I_{avg}$
-  receive colorbar values of 1. We apply the same scaling method to the simulated
-  patterns. We carefully chose a scaling factor of 2.5 in order to (1) visibly
-  display all features in the experimental pattern and (2) to allow us to compare
-  the relative intensities of features between simulated and experimental
-  diffraction patterns.
+  from experiment in those regions.  Specifically, in contrast to the
+  experimental WAXS pattern, R-$\pi$ appearing in simulated diffraction patterns
+  intersects with R-alkanes (See Fig. \ref{fig:XRDsim}). We multiplied $I_{avg}$
+  by a scaling factor of 2.5. Intensities that appear in the experimental pattern
+  $\geq$ 2.5$I_{avg}$ receive colorbar values of 1. We apply the same scaling
+  method to the simulated patterns. We carefully chose a scaling factor of 2.5 in
+  order to (1) visibly display all features in the experimental pattern and (2)
+  to allow us to compare the relative intensities of features between simulated
+  and experimental diffraction patterns.
 
@@
 %MRS4: yeah, probably. Possibly supplemental information.
-  \begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwiched.png}
-		\caption{}\label{fig:sandwiched}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{PD.png}
-		\caption{}\label{fig:pd}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{Tshaped.png}
-		\caption{}\label{fig:tshaped}
-	\end{subfigure}
-	\vskip\baselineskip
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{sandwichedlayers.png}
-		\caption{}\label{fig:sandwichedlayers}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.475\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{offsetlayers.png}
-		\caption{}\label{fig:offsetlayers}
-	\end{subfigure}
-	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
-	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
-	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
-	configuration }\label{fig:stacking}
-  \end{figure}
+%  \begin{figure}
+%	\centering
+%	\begin{subfigure}[b]{0.32\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{sandwiched.png}
+%		\caption{}\label{fig:sandwiched}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.32\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{PD.png}
+%		\caption{}\label{fig:pd}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.32\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{Tshaped.png}
+%		\caption{}\label{fig:tshaped}
+%	\end{subfigure}
+%	\vskip\baselineskip
+%	\begin{subfigure}[b]{0.475\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{sandwichedlayers.png}
+%		\caption{}\label{fig:sandwichedlayers}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.475\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{offsetlayers.png}
+%		\caption{}\label{fig:offsetlayers}
+%	\end{subfigure}
+%	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
+%	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
+%	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
+%	configuration }\label{fig:stacking}
+%  \end{figure}
 
@@
 		in each layer increases. The pore spacing of a system starting in the
-		sandwiched configuration is systematically 
-%MRS4: added
-slightly
-lower than that started in an offset
-		configuration. }~\label{fig:p2p}
+		sandwiched configuration is systematically slightly lower than that started in
+		an offset configuration. }~\label{fig:p2p}
   \end{figure}
@@
 
-%MRS3: maybe the ``R-spots'' signal, to get agreement in number for grammar. Check other instances.
   The R-spots signal, which appears in both simulated XRD patterns, is a result
@@
         %MRS4: did you use a different scaling for the color bar here than above? If so, mention.
+        %BJC3: The scaling is the same
   \end{figure}
@@
 or ``more disordered''?
+%BJC3: agreed, I'll stick with disordered pores
 %  The $z$-direction correlation functions show that layers in our model prefer
 %  to stack further apart than 3.7 \angstrom~as suggested by experiment.
-  When systems are built with layers stacked 5.0 \AA~apart then
-  equilibrated, we observe long-term stability of a qualitatively different
-  configuration, suggesting that we have found another metastable free energy
-  basin, further corroborating (\ref{point:metastable}). We studied this type of
-  system in both the parallel displaced and sandwiched configurations.
-
-  Structural properties are different when layers are initially spaced 5 \AA~
-  apart. In both configurations, we observe a decrease in pore spacing
-  (Fig.~\ref{fig:p2p_disordered}) and a corresponding increase in the equilibrated
-  distance between layers (Fig.~\ref{fig:dbwl_disordered}). The simulated X-ray
-  diffraction patterns indicate further structural differences. In the parallel
-  displaced configuration, almost all contrast between R-spots and R-alkanes is faded
-  (Fig. ~\ref{fig:offset_disordered_xrd}). In the sandwiched
-  configuration, R-spots is weakly present, but in different locations, showing higher
-  intensity at the top and bottom of the pattern as well as at the intersection
-  of R-alkanes with q$_z$ = 0 (Fig. ~\ref{fig:layered_disordered_xrd}).
+  When systems are built with layers stacked 5.0 \AA~apart then equilibrated,
+  we observe long-term stability of a qualitatively different configuration,
+  suggesting that we have found another metastable free energy basin, further
+  corroborating (\ref{point:metastable}). For reasons to become aparent later,
+  we will refer to this class of systems as the disordered pore basin. 
+  Systems with layers initially stacked 3.7 \AA~apart will be referred to
+  as the ordered basin. We studied each basin in both the parallel
+  displaced and sandwiched configurations.
+
+%  Structural properties are different when layers are initially spaced 5 \AA~
+%  apart. 
+  Structural properties are different in the disordered pore basin.  In both
+  configurations, we observe a decrease in pore spacing
+  (Fig.~\ref{fig:p2p_disordered}) and a corresponding increase in the
+  equilibrated distance between layers (Fig.~\ref{fig:dbwl_disordered}). The
+  simulated X-ray diffraction patterns indicate further structural differences.
+  In the parallel displaced configuration, almost all contrast between R-spots
+  and R-alkanes is faded (Fig. ~\ref{fig:offset_disordered_xrd}). In the
+  sandwiched configuration, R-spots is weakly present, but in different
+  locations, showing higher intensity at the top and bottom of the pattern as
+  well as at the intersection of R-alkanes with q$_z$ = 0 (Fig.
+  ~\ref{fig:layered_disordered_xrd}).
 
@@
         \end{subfigure}
-	\caption{In comparison to systems built with 3.7 \AA~initial layer spacing,  
-                the simulated X-ray diffraction patterns of the parallel displaced (a) and 
- 		sandwiched (b) configurations are different when systems are built with 
- 		a 5 \AA~initial layer spacing, most notably in the region bounded by R-alkanes.
-      		When layers are stacked further apart, the distance between layers increases (c)
-                and the pore spacing decreases (d).}
+	\caption{In comparison to the ordered pore systems ,  the simulated
+		X-ray diffraction patterns of the parallel displaced (a) and sandwiched (b)
+		configurations are different than the disordered pore systems , most notably in
+		the region bounded by R-alkanes.  When layers are initially stacked further
+		apart, the distance between layers increases (c) and the pore spacing decreases
+		(d).}
   \end{figure}
@@
   In all cases, the space in the pore region is filled with sodium ions and
-  head groups. When systems are spaced 3.7 \AA~apart, there is less density in
-  the center of the pore indicating a more ordered pore structure. In both the
-  sandwich and parallel displaced configurations, we see the density of head
-  groups and sodium ions fall to less than 50\% of its maximum at r = 0
+  head groups. In ordered pore systems , there is less density in the center of
+  the pore indicating a more ordered pore structure. In both the sandwich and
+  parallel displaced configurations, we see the density of head groups and sodium
+  ions fall to less than 50\% of its maximum at r = 0
   (Fig.~\ref{fig:layered_density}). The situation is most pronounced in the
-  sandwiched configuration where the maximum head group density occurs 0.44 nm from the pore
-  center. The parallel displaced configuration reaches its maximum 0.35 nm from
-  the pore center. In contrast, both system built with layers initially spaced
-  5 \AA~apart show very little difference in density from its maximum. This 
-  implies a more uniform distribution of head groups within the pore center. 
+  sandwiched configuration where the maximum head group density occurs 0.44 nm
+  from the pore center. The parallel displaced configuration reaches its maximum
+  0.35 nm from the pore center. In contrast, both disordered pore systems show
+  very little difference in density from its maximum. This implies a more uniform
+  distribution of head groups within the pore center. 
   % High vacancy is less likely to be stable in the real system
@@
   and head groups are not confined to just within the pore region. In all cases,
-  19\% of sodium ions exist outside the pore region whose radius is assumed to
-  be 0.6 nm for this calculation (except sandwiched, 3.7 \AA~initial layer
-  spacing, where 16\% are outside the pore). Additionally, we see that in all
-  cases, about 3\% of the plotted tail density is located within the pore region
-  (except sandwiched, 3.7 \AA~initial layer spacing, where 1.5\% are within the
-  pore region). These observations bring into question how one should define a
-  pore in these types of systems. One usually measures a membrane's pore radius
-  based on the size of a molecule it can reject, however it is not clear where
-  the edges of the pores are and what size molecule would fit through. We leave
-  these investigations for a future study.
+  19\% of sodium ions exist outside the pore region whose radius is assumed to be
+  0.6 nm for this calculation (except sandwiched, ordered pore , where 16\% are
+  outside the pore). Additionally, we see that in all cases, about 3\% of the
+  plotted tail density is located within the pore region (except sandwiched,
+  ordered pore, where 1.5\% are within the pore region). These observations bring
+  into question how one should define a pore in these types of systems. One
+  usually measures a membrane's pore radius based on the size of a molecule it
+  can reject, however it is not clear where the edges of the pores are and what
+  size molecule would fit through. We leave these investigations for a future
+  study.
 
@@
 
-  In all cases, water disrupts structuring of the model. The plots in Figure~\ref{fig:solvation} 
-  are normalized to have the same colorbar as the dry
-  systems. 
-  %MRS4: not quite sure what it means to be normalized to have the same colorbar?
-  The intensity of the reflections decrease when water is added to the
-  system. In systems built with 5\% wt water, R-$\pi$ and R-spots
-  become nearly indistinguishable from R-alkanes.
+  In all cases, water disrupts structuring of the model \ref{fig:solvation}.
+  The intensity of the reflections decrease when water is added to the system. In
+  systems built with 5\% wt water, R-$\pi$ and R-spots become nearly
+  indistinguishable from R-alkanes.
 
@@
   dry systems, we see a gradual compositional transition from hydrophilic to hydrophobic.  
-  We see that the pores become a soup of water molecules and sodium ions (Fig.
+  We see that the pores become a mixture of water molecules and sodium ions (Fig.
   \ref{fig:water_density}).
-  %MRS4: soup is too colloquial.
 
@@
   %MRS4: weird there's a head group peak in the center. Not enough statistics, so shot noise from the r^2 dr weighting?
+  %BJC3: Yea, I'm not sure exactly. I'll look more into it. It might one or two head groups that just get stuck there.
+  % The pore I picture in the supplemental info is completely cleared of any head groups.
+
   \subsection{Model Ionic Conductivity Measurements}
@@
   per layer and an initial layer spacing of 3.7 \AA.  
-  %MRS4: do we have a sense of how consistent this behavior is?
-I.e.
-if started with 4 apart does it look like 3.7 or 5 separations?
-How about 4.5?
-Is there a gradual range of changes?
-Can we rule this out?
-What work was done on this?
+  % MRS4: do we have a sense of how consistent this behavior is? I.e. if
+  % started with 4 apart does it look like 3.7 or 5 separations? How about 4.5?
+  % Is there a gradual range of changes? Can we rule this out? What work was
+  % done on this?
+  % BJC3: I'll get back to you
 
@@
   learned that the pores are generally filled by monomer head groups and sodium
-  ions. Membranes prepared in the sandwiched configuration have more 
-  %MRS4: lower-density instead of vacant?
-  vacant
+  ions. Membranes prepared in the sandwiched configuration have lower density 
   pores. We also observed that there is not a hard partition between hydrophlic

### 2017-12-19 Ben_Manuscripts/structure_paper/Draft.tex
Added references, new solvat

@@
 
-  Current commercial RO and NF membranes suffer from inherent limitations of
-  their fabrication. Although scalable, each process has a degree of
-  stochasticity which makes overcoming the permeability-selectivity tradeoff a
-  challenge. Namely, it is difficult to increase the permeability of a desired
-  species, while maintaining the same retention of an undesired species.
+  Current commercial RO and NF membranes suffer limitations inherent to their
+  fabrication. Although scalable, each process has a degree of stochasticity
+  which makes overcoming the permeability-selectivity tradeoff a challenge.
+  Namely, it is difficult to increase the permeability of a desired species,
+  while maintaining the same retention of an undesired species
+  \cite{werber_materials_2016}.
 
@@
 
-  Commercial RO membranes are thin film composite membranes with a porous
-  support layer and an active layer made of a polymer matrix formed by
-  interfacial polymerization. During synthesis, a step-growth polymerization
-  reaction occurs at the interface of an aqueous monomer solution, which has been
-  soaked into the support layer, and an organic solution of a second monomer. The
-  polymer matrix is dense and highly crosslinked which gives high rejections but
-  low permeability.
+  Commercial RO membranes are typically thin film composite membranes with a
+  porous support layer and an active layer made of a polymer matrix formed
+  through interfacial polymerization \cite{jeong_interfacial_2007}. During
+  interfacial polymerization, a step-growth polymerization reaction occurs at the
+  interface of an aqueous monomer solution, which has been soaked into the
+  support layer, and an organic solution of a second monomer. The polymer matrix
+  is dense and highly crosslinked which gives high rejections but low
+  permeability.
 
@@
 %  During phase inversion, a thin polymer film is precipitated out of a polymer
-  NF membranes are typically made by a phase inversion process. The most widely
+  NF membranes are typically made by a phase inversion process  The most widely
   used phase inversion process is immersion precipitation, during which a polymer
   dissolved in a solvent is submerged in a non-solvent. A solid, porous membrane
-  is all that remains once all solvent has been removed by non-solvent exchange. 
-  Resultant pores are polydisperse in size which hurts membrane selectivity.  A
-  second technique used to create NF membranes is call track etching in which a
-  polymer film is bombarded with charged particles, then chemically etched to
-  create pores. The pores are uniform which benefits selectivity, however the
-  membranes have a low porosity and subsequent low permeability.
+  is all that remains once all solvent has been removed by non-solvent exchange
+  \cite{smolders_microstructures_1992}.  Resultant pores are polydisperse in size
+  which hurts membrane selectivity. A second technique used to create NF
+  membranes is call track etching in which a polymer film is bombarded with
+  charged particles, then chemically etched to create pores
+  \cite{apel_track_2001}. The pores are uniform which benefits selectivity,
+  however the membranes have a low porosity and subsequently low permeability.
 
@@
   nanotubes show promise \cite{humplik_nanostructured_2011} but synthetic
-  techniques are unable to achieve scalable alignment and pore monodispersity.
-  \cite{hata_water-assisted_2004,maruyama_growth_2005} Zeolites have sub-nm pores
+  techniques are unable to achieve scalable alignment and pore monodispersity
+  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Zeolites have sub-nm pores
   with a narrow pore size distribution and MD simulations exhibit complete
-  rejection of solvated ions, \cite{murad_molecular_1998} however, experimental
+  rejection of solvated ions \cite{murad_molecular_1998}, however, experimental
   rejection was low and attributed to interstitial defects formed during membrane
-  synthesis. \cite{li_desalination_2004} There is a need for a scalable
+  synthesis \cite{li_desalination_2004}. There is a need for a scalable
   nanostructured membrane.
@@
   added benefits of low cost and synthetic techniques feasible for large scale
-  production.  \cite{feng_scalable_2014} LLC systems created by the monomer
+  production \cite{feng_scalable_2014}. LLC systems created by the monomer
   Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied
-  experimentally.
-  \cite{smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}
+  experimentally
+  \cite{feng_scalable_2014,smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_thin_2016}.
   Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h} phase
@@
   crosslinking to lock the structure in place \cite{feng_scalable_2014}. In 2016,
-  Feng et al.~showed that the same result could be obtained using a technique
+  Feng et al. showed that the same result could be obtained using a second technique
   termed soft confinement \cite{feng_thin_2016}.
@@
 	hydrophilic head groups (blue) facing towards the disk center. The disks
-	assemble into hexagonally packed columnar mesophases (e)}~\label{fig:assembly}
+	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
   \end{figure}
@@
   (Fig. \ref{fig:detail}), assuming the force fields are sufficiently accurate.
-  with such an atomistic model, We can directly observe solute transport and
+  With such an atomistic model, we can directly observe solute transport and
   suggest governing mechanisms. We can observe how the choice of head group may
@@
   phases appear to share similar structural characteristics since the pore 
-  spacings in each system are in close agreement \cite{resel_structural_2000,feng_thin_2016}.
+  spacings in each system are in close agreement \cite{feng_thin_2016,resel_structural_2000}.
 
@@
   cannot definitively answer. Our current level of understanding suggests that
-  monomers partition into layers with head groups facing the center, then 
+  monomers partition into layers with head groups facing towards the center, then 
   stack on top of each other to create pores that pack together hexagonally.
   There are several key questions that we will investigate in order to
-  expand our understanding.
+  expand this understanding:
 
@@
   and T-shaped $\pi$-$\pi$ stacking conformations versus a sandwiched
-  conformation ~\cite{sinnokrot_estimates_2002}. Substituted benzene rings
+  conformation \cite{sinnokrot_estimates_2002}. Substituted benzene rings
   exhibit an even stronger $\pi$-$\pi$ stacking attraction which favors the
@@
   are extremely electron withdrawing.
-  \cite{waller_hybrid_2006,ringer_effect_2006}. In this study, we compare
+  \cite{waller_hybrid_2006,ringer_effect_2006} In this study, we compare
   simulated X-ray diffraction patterns to experiment in order to deduce which
-  stacking configurations is most likely.
+  stacking configuration is most likely.
 
@@
 
-  	\item A weak intensity line is located at exactly half the $q_z$ value of
-	R-$\pi$ ($q_z$ = 0.85 \angstrom$^{-1}$), corresponding to a real space periodic
-	spacing of 7.4 \angstrom~. This reflection has been interpreted as
-	2\textsubscript{1} helical ordering of aromatic rings along the z axis, meaning
-	that if the positions of the aromatic rings can be traced by a helix, then for
-	each full turn in the helix, one will encounter two aromatic rings. For this
-	reason it will be referred to as R-helix.
+	\item A weak intensity line is located at exactly half the $q_z$ value
+	of R-$\pi$ ($q_z$ = 0.85 \angstrom$^{-1}$), corresponding to a real space
+	periodic spacing of 7.4 \angstrom~. This reflection has been interpreted as
+	2\textsubscript{1} helical ordering of aromatic rings along the z axis
+	\cite{feng_scalable_2014}, meaning that if the positions of the aromatic rings
+	can be traced by a helix, then for each full turn in the helix, one will
+	encounter two aromatic rings. For this reason it will be referred to as
+	R-helix.
 
@@
 	4.5 \angstrom~ which is characteristic of the average spacing between packed
-	alkane chains.  This reflection will be called R-alkanes.
+	alkane chains \cite{mcintosh_organization_1980}. This reflection will be called
+	R-alkanes.
 
@@
 	explained by the tilt angle of the alkane chains with respect to the membrane
-	plane.
+	plane \cite{govind_simple_2001}.
 
@@
 	= 0. The spacing between dots is indicative of the hexagonal symmetry of the
-	packed pores. The same information at higher resolution is obtained using SAXS.
+	packed pores. The same information at higher resolution is obtained using SAXS (Fig.~\ref{fig:SAXS}).
 
@@
 %BJC3: Got it, will do once I have more time to focus on figures 
-	\caption{(a) The repeat spacing in the 1D small angle X-ray scattering pattern
-		is characteristic of hexagonal packing. The leading peak represents the
-		distance between the d\textsubscript{100} planes. Using this distance, we know
-		that the distance between pore centers is 4.12 nm. (b) 2D wide angle X-ray
-		scattering gives details about repeating features less than 1 nanometer
-		apart. Experimentalists have justified each of the 5 major reflections
-		present as follows: (I) Aromatic head group $\pi-\pi$ stack 3.7 \AA~apart.
-		(II) Monomers arrange vertically in a 2\textsubscript{1} helix. (III) Alkane
- 		chain tails pack 4.5 \AA~apart. (IV) Monomer tails tilt with respect to the 
- 		membrane plane. (V) As derived from SAXS, pores pack hexagonally and are 
-		spaced 4.12 nm apart}
+	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
+		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
+		packing. The leading peak represents the distance between the
+		d\textsubscript{100} planes. Using this distance, we know that the distance
+		between pore centers is 4.12 nm. (b) 2D wide angle X-ray scattering gives
+		details about repeating features less than 1 nanometer apart. Experimentalists
+		have justified each of the 5 major reflections present as follows: (I) Aromatic
+		head group $\pi-\pi$ stack 3.7 \AA~apart.  (II) Monomers arrange vertically in
+		a 2\textsubscript{1} helix. (III) Alkane chain tails pack 4.5 \AA~apart. (IV)
+		Monomer tails tilt with respect to the membrane plane. (V) As derived from
+		SAXS, pores pack hexagonally and are spaced 4.12 nm apart}
 	\label{fig:SWAXS}
@@
   method of \texttt{molcharge} shipped with QUACPAC from Openeye Scientific
-  Software. All molecular dynamics simulations were run using Gromacs 2016.
-  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-  the experiments.  An ensemble of characteristic, low-energy vacuum monomer
+  Software. All molecular dynamics simulations were run using Gromacs 2016
+  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
+  An ensemble of characteristic, low-energy vacuum monomer
   configurations were constructed by applying a simulated annealing process to a
@@
 		configuration. (b) Monomers are rotated and assembled into layers with 
-		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
+		hydrophilic centers. (c) Twenty layers are stacked on top of each other to create
 		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
@@
   periodically. Each pore is made of twenty stacked monomer layers with periodic
-  continuity in the z direction, avoiding any edge effects and creating an
+  continuity along the pore axis, avoiding any edge effects and creating an
   infinite length pore ideal for studying transport. A small number of layers is
@@
   chosen to be 0.6 nm in our initial configurations because the pore size is
-  estimated to be $\approx$ 1.2 nm \cite{zhou_supported_2005}.  The initial
-  distance between pores also has little effect on the the equilibrated
-  structure. However, one should not start them too close or there will be high
-  energy repulsions during early equilibration. We chose an initial pore spacing
-  of 4.5 nm, $\sim$10\% larger than the experimental value of 4.12 nm.  The
-  distance between layers, the rotation of the layers with respect to adjacent
-  layers, and the number of monomers per layer do influence the equilibrium
-  structure and require further justification for their choices.  We rely on
-  experimental data to inform them.
+  estimated to be $\sim$1.2 nm \cite{zhou_supported_2005}. The initial distance
+  between pores also has little effect on the the equilibrated structure (See
+  supplemental information). However, one should not start them too close or
+  there will be high energy repulsions during early equilibration. We chose an
+  initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
+  of 4.12 nm.  The distance between layers, the rotation of the layers with
+  respect to adjacent layers, and the number of monomers per layer do influence
+  the equilibrium structure and require further justification for their choices.
+  We rely on experimental data to inform them.
 
@@
   substituted benzene rings: sandwiched, parallel-displaced and T-shaped
-  ~\cite{sinnokrot_estimates_2002} (\Cref{fig:sandwiched,fig:pd,fig:tshaped}).
+  \cite{sinnokrot_estimates_2002} (Fig. \ref{fig:sandwiched} and \ref{fig:pd,fig:tshaped}).
   The T-shaped configuration was ruled out because its $\sim$5 \angstrom~
-  equilibrium stacking distance ~\cite{sinnokrot_estimates_2002} is inconsistent
+  equilibrium stacking distance \cite{sinnokrot_estimates_2002} is inconsistent
   with R-$\pi$. It is also infeasible for the monomers to orient in the T-shaped
@@
 
-  The number of monomers in each layer is unknown, as state in
+  The number of monomers in each layer is unknown, as stated in
   (\ref{point:monomernum}). We tested configurations constructed with a varied
@@
   atoms are changed to appropriate hydrogen types. Head-to-tail addition was the
-  only propagation mode considered due to its dominance in the real system.
+  only propagation mode considered due to its dominance in the real system \cite{young_introduction_2011}.
   Direction of attack was not considered because the resultant mixture is
@@
 
-  Our implementation requires long simulation times to achieve high degrees of
-  crosslinking. A typical crosslinking procedure can take up to 24 hours. In
+  Our implementation requires long simulation times to achieve high crosslink 
+  densities. A typical crosslinking procedure can take up to 24 hours. In
   order to collect equilibrated data, further NPT simulation is necessary. We
@@
   Using equilibrated structures, we carry out various calculations to
-  characterize the system. We define the point at which a system is
-  equilibrated based on when the distance between pores stops changing.
-  We determined when the distances stopped changing by applying the statistical
-  test, \texttt{pymbar.timeseries.detectEquilibration}, to the time series. 
-  Simulations of 400 ns give at least 50 ns of equilibrated simulation trajectory.
-  %BJC2: Do I cite the github repository for pymbar?
-  %MRS4, yes, though also http://pubs.acs.org.colorado.idm.oclc.org/doi/abs/10.1021/acs.jctc.5b00784
+  characterize the system. We define the point at which a system is equilibrated
+  based on when the distance between pores stops changing.  We determined when
+  the distances stopped changing by applying the statistical test,
+  \texttt{pymbar.timeseries.detectEquilibration}, to the time series
+  \cite{chodera_simple_2016,shirts_statistically_2008}.  Simulations of 400 ns
+  give at least 50 ns of equilibrated simulation trajectory.
+
   To calculate the equilibrated pore spacing, we measured the distance between
@@
   charge transfer through the system and can be thought to represent the center
-  of charge of the system. The conductance, $\gamma$ of the system can be
+  of charge of the system. The conductance, $\gamma$, of the system can be
   calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic
@@
   the closest match to experiment. It produces the only pattern that exhibits all
-  major reflections. R-alkanes and R-pores appear as they do in the
-  sandwiched configuration. R-spots and R-$\pi$ appears, however with a lower intensity relative to
-  R-alkanes when compared to the sandwiched configuration. R-helix appears due to
-  the parallel displaced aromatic rings. It is a subharmonic of R-$\pi$ since the
-  nearest vertically stacked head group to any given head group is 7.4 \AA~away.
+  major reflections. R-alkanes and R-pores appear as they do in the sandwiched
+  configuration. R-spots and R-$\pi$ appear, however with a lower intensity
+  relative to R-alkanes when compared to the sandwiched configuration. R-helix
+  appears due to the parallel displaced aromatic rings. It is a subharmonic of
+  R-$\pi$ since the nearest vertically stacked head group to any given head group
+  is 7.4 \AA~away.
 
@@
   appropriately model the aromatic interactions which would be necessary to
-  achieve the correct $\pi$-$\pi$ stacking distance. Systems have been modeled
-  that exhibit the correct stacking distance, however they are typically made of
-  planar molecules spanning a large area. The system we have modeled has bulky
-  tails whose entropic contributions compete with the $\pi$-$\pi$ stacking
-  interaction energy.  There have been efforts to model systems that contain
-  $\pi$ interactions in a classical mechanical context using polarizable
-  forcefields. 
-%MRS3: cite specific efforts on treatment if pi-stacking. 
-%MRS4: i.e. add citations.
-We could implement a polarizable force field, however it is likely
-  not worth the extra computational cost. If our model proves to be inadequate
-  when simulating transport, we will revisit our current choice of forcefield.
+  achieve the correct $\pi$-$\pi$ stacking distance. 
+  %Systems have been modeled that exhibit the correct stacking distance, however
+  %they are typically made of planar molecules spanning a large area.
+  %BJC: I saw a paper like this a long time ago, but failed to save the citation and
+  % now I am having a hard time finding it again. 
+  The system we have modeled has bulky tails whose entropic contributions compete
+  with the $\pi$-$\pi$ stacking interaction energy.  There have been efforts to
+  model systems that contain $\pi$ interactions in a classical mechanical context
+  using polarizable forcefields \cite{baker_polarizable_2015}.  We could
+  implement a polarizable force field, however it is likely not worth the extra
+  computational cost. If our model proves to be inadequate when simulating
+  transport, we will revisit our current choice of forcefield.
 
@@
   In the parallel displaced configuration, almost all contrast between R-spots
-  and R-alkanes is faded (Fig. ~\ref{fig:offset_disordered_xrd}). In the
+  and R-alkanes is faded (Fig.~\ref{fig:offset_disordered_xrd}). In the
   sandwiched configuration, R-spots is weakly present, but in different
@@
         \end{subfigure}
-	\caption{In comparison to the ordered pore systems ,  the simulated
+	\caption{In comparison to the ordered pore systems, the simulated
 		X-ray diffraction patterns of the parallel displaced (a) and sandwiched (b)
@@
   In all cases, the space in the pore region is filled with sodium ions and
-  head groups. In ordered pore systems , there is less density in the center of
+  head groups. In ordered pore systems, there is less density in the center of
   the pore indicating a more ordered pore structure. In both the sandwich and
@@
 
-  We explored the affect of water on pore structure, addressing \ref{point:water}
+  We explored the affect of water on pore structure, addressing (\ref{point:water})
 %  We answered (\ref{point:water}) and further support (\ref{point:orientation})
@@
 
-  % BJC: TODO: reformat
-  %            adjust colorbar
+  % formatting taken from : https://tex.stackexchange.com/questions/239715/add-titles-for-rows-and-columns-in-a-subfloat
+  \newlength{\tempdima}
+  \newcommand{\rowname}[1]% #1 = text
+  {\rotatebox{90}{\makebox[\tempdima][c]{\textbf{#1}}}}
+
+  \renewcommand{\thesubfigure}{\alph{subfigure}}
+  \newcommand{\mycaption}[1]% #1 = caption
+  {\refstepcounter{subfigure}\textbf{(\thesubfigure) }{\ignorespaces #1}}
+
   \begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
-        %MRS2: include 0% as well? Maybe leave off 5% if not relevant in the end?
-	\caption{}
+  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
+  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
+  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
+  	\rowname{parallel displaced}&
+  	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_1.png}&
+  	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_25.png}&
+  	\includegraphics[width=.325\linewidth]{solvated_offset_rzplot_5.png}\\[-1ex]
+  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
+  	\rowname{sandwiched}&
+  	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_1.png}&
+  	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_25.png}&
+  	\includegraphics[width=.325\linewidth]{solvated_layered_rzplot_5.png}\\[-1ex]
+  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
+  	\end{tabular}
+  	\caption{simulated diffraction patterns generated from trajectories of systems 
+  	built in the parallel displaced and sandwiched configurations as a function
+  	of water content shows weaker reflections than the dry system.}%
   \label{fig:solvation}
+
   \end{figure}
@@
   The intensity of the reflections decrease when water is added to the system. In
-  systems built with 5\% wt water, R-$\pi$ and R-spots become nearly
+  systems built with 5 wt\% water, R-$\pi$ and R-spots become nearly
   indistinguishable from R-alkanes.
@@
 
-  In systems built with 5\% wt water, the pore region becomes filled with
+  In systems built with 5 wt\% water, the pore region becomes filled with
   water. We plotted the number density of components in this system. As with the 
@@
   group density shifts from 0.35 to 0.62 nm and from 0.44 to 0.61 nm in the
-  parallel displaced and sandwiched configurations respectively.  We observe the
-  existence of ions, head groups and water outside the pore region. In the
+  parallel displaced and sandwiched configurations respectively. Again, we observe the
+  existence of ions, head groups and water outside the pore region, however in the
   hydrated system, the head groups drift beyond 1.5 \AA~from the pore center. In
@@
   This system is a closer representation of the H\textsubscript{II} phase which
-  is typically synthesized with ca. 8\% wt water. Further investigation of
+  is typically synthesized with ca. 8 wt\% water. Further investigation of
   hydrated systems can help unravel the mechanisms for selective transport in
@@
   which we are comparing was done on a \SI{80}{\micro\metre} thick film, nearly
-  10,000 times thicker than our simulated system. The thick film likely has
-  defects leading to non-contiguous pores and imperfect alignment.  It has been
-  shown that there is a large dependence of ionic conductivity on the alignment
-  of the pores. The ionic conductivity of an unaligned film is ca. 85 times lower
-  than that of a nearly aligned film referenced here. We hypothesize that a thin,
-  perfectly aligned film would have a value of ionic conductivity in closer
-  agreement with our model.
+  10,000 times thicker than our simulated system. The thick film is likely
+  imperfectly aligned and has defects leading to non-contiguous pores. It has
+  been shown that there is a large dependence of ionic conductivity on the
+  alignment of the pores. The ionic conductivity of an unaligned film is ca. 85
+  times lower than that of a nearly aligned film referenced here. We hypothesize
+  that a thin, perfectly aligned film would have a value of ionic conductivity in
+  closer agreement with our model.
 

### 2017-12-19 Ben_Manuscripts/structure_paper/supplemental.tex
Modifications based on comments
Added references, new solvat

@@
         \centering
+        \begin{subfigure}[b]{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{sandwiched.png}
+                \caption{}\label{fig:sandwiched}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{PD.png}
+                \caption{}\label{fig:pd}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{Tshaped.png}
+                \caption{}\label{fig:tshaped}
+        \end{subfigure}
+        \vskip\baselineskip
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{sandwichedlayers.png}
+                \caption{}\label{fig:sandwichedlayers}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{offsetlayers.png}
+                \caption{}\label{fig:offsetlayers}
+        \end{subfigure}
+        \caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
+        3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart.
+        (d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
+        configuration }\label{fig:stacking}
+  \end{figure}
+
+  \begin{figure}
+	\centering
         \includegraphics[width=0.9\textwidth]{monomer.png}
@@
 
+  \begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{pore_radius_illustration.png}
+	\caption{When creating an initial configuration, the pore radius is defined based
+	on the distance of the carbonyl carbon from the pore's central axis}
+	\label{fig:pore_radius_illustration}
+  \end{figure}
+
+  \textbf{TODO} : These are things I am working on / need to do
+
+  \begin{itemize}
+  \item Initial configuration dependence
+	\begin{itemize}
+		\item Initial pore-to-pore spacing
+		\item Initial pore radius
+		\item I have simulations running to support the claims that
+		these are not significant factors if chosen within reason. And
+		I will define what is meant by 'within reason'.
+	\end{itemize}
+  \item Description of parameterization process
+  \item Feel free to suggest anything else that might be useful
+  \end{itemize}
+
+  \textbf{Calculation of pore-to-pore spacing statistics}
+
+  \color{red}{This is an outline of this section and will be reworded for clarity}
   \begin{itemize}

### 2018-01-02 Ben_Manuscripts/structure_paper/Draft.tex
Incorporated Gin comments

@@
 
-  Nanostructured membrane materials have become increasingly popular for
+  Nanostructured porous membrane materials have become increasingly popular for
   aqueous separations applications such as desalination and biorefinement because
-  they offer the ability to control membrane architecture at the atomic scale
-  permitting the design of solute-specific separation membranes
+  they offer the ability to control pore architecture at the molecular scale,
+  thereby permitting the design of solute-specific separation membranes
   \cite{humplik_nanostructured_2011}. Most membrane-based aqueous separations of
@@
 
-  Current commercial RO and NF membranes suffer limitations inherent to their
-  fabrication. Although scalable, each process has a degree of stochasticity
-  which makes overcoming the permeability-selectivity tradeoff a challenge.
-  Namely, it is difficult to increase the permeability of a desired species,
-  while maintaining the same retention of an undesired species
-  \cite{werber_materials_2016}.
+  Current commercial RO and NF membranes suffer from limitations inherent to
+  their fabrication. Although scalable, each of these two types of membranes has
+  a degree of stochasticity that makes overcoming the permeability-selectivity
+  tradeoff a challenge.  Namely, it is difficult to increase the permeability of
+  a desired molecular or atomic species, while maintaining the same retention of
+  an undesired species \cite{werber_materials_2016}.
 
@@
 
-  Commercial RO membranes are typically thin film composite membranes with a
-  porous support layer and an active layer made of a polymer matrix formed
-  through interfacial polymerization \cite{jeong_interfacial_2007}. During
-  interfacial polymerization, a step-growth polymerization reaction occurs at the
-  interface of an aqueous monomer solution, which has been soaked into the
+  Commercial RO membranes are typically dense thin-film composite (TFC)
+  membranes with a porous support layer and an active layer made of a polymer
+  matrix formed through interfacial polymerization \cite{jeong_interfacial_2007}.
+  During interfacial polymerization, a step-growth polymerization reaction occurs
+  at the interface of an aqueous monomer solution that has been soaked into the
   support layer, and an organic solution of a second monomer. The polymer matrix
-  is dense and highly crosslinked which gives high rejections but low
+  is dense and highly cross-linked which gives high rejections but low
   permeability.
@@
 %  During phase inversion, a thin polymer film is precipitated out of a polymer
-  NF membranes are typically made by a phase inversion process  The most widely
-  used phase inversion process is immersion precipitation, during which a polymer
-  dissolved in a solvent is submerged in a non-solvent. A solid, porous membrane
-  is all that remains once all solvent has been removed by non-solvent exchange
-  \cite{smolders_microstructures_1992}.  Resultant pores are polydisperse in size
-  which hurts membrane selectivity. A second technique used to create NF
-  membranes is call track etching in which a polymer film is bombarded with
+  NF membranes are typically porous membranes made by a phase-inversion
+  process.  The most widely used phase-inversion process is immersion
+  precipitation, during which a polymer dissolved in a solvent is submerged in a
+  non-solvent. A solid, porous polymer membrane is all that remains once all
+  solvent has been removed by non-solvent exchange
+  \cite{smolders_microstructures_1992}.  The resultant pores are polydisperse in
+  size, which hurts membrane selectivity. A second technique used to create NF
+  membranes is call track-etching in which a polymer film is bombarded with
   charged particles, then chemically etched to create pores
-  \cite{apel_track_2001}. The pores are uniform which benefits selectivity,
-  however the membranes have a low porosity and subsequently low permeability.
+  \cite{apel_track_2001}. The pores are uniform, which benefits selectivity;
+  however, the membranes have a low porosity and subsequently low permeability.
 
@@
   The permeability-selectivity tradeoff has the potential to be overcome by
-  designing membranes at the molecular level. Next-generation nanostructured
+  designing membranes at the molecular level. Next-generation nanoporous
   membranes with high selectivity permitted by a precisely controlled pore size
@@
 
-  Development of nanostructured materials has been limited by the ability to
-  synthesize and scale various fundamentally sound technologies. Graphene sheets
-  are atomically thick which results in excellent water permeability but defects
-  during manufacturing severely impact selectivity
-  \cite{cohen-tanugi_multilayer_2016}. Molecular dynamics (MD) simulations of carbon
-  nanotubes show promise \cite{humplik_nanostructured_2011} but synthetic
+  Development of nanostructured porous materials has been limited by the
+  ability to synthesize and scale various fundamentally sound technologies.
+  Graphene sheets are atomically thick which results in excellent water
+  permeability but defects during manufacturing severely impact selectivity
+  \cite{cohen-tanugi_multilayer_2016}. Molecular dynamics (MD) simulations of
+  carbon nanotubes show promise \cite{humplik_nanostructured_2011}, but synthetic
   techniques are unable to achieve scalable alignment and pore monodispersity
-  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Zeolites have sub-nm pores
-  with a narrow pore size distribution and MD simulations exhibit complete
-  rejection of solvated ions \cite{murad_molecular_1998}, however, experimental
-  rejection was low and attributed to interstitial defects formed during membrane
-  synthesis \cite{li_desalination_2004}. There is a need for a scalable
-  nanostructured membrane.
-
-  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
-  aqueous separation applications. LLCs share the characteristic ability of
-  nanostructured membrane materials to create highly ordered structures with the
-  added benefits of low cost and synthetic techniques feasible for large scale
+  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Zeolites have sub-nm
+  pores with a narrow pore size distribution, and MD simulations of these
+  materials show that they exhibit complete rejection of solvated ions
+  \cite{murad_molecular_1998}- however, experimental rejection was low and
+  attributed to interstitial defects formed during membrane synthesis
+  \cite{li_desalination_2004}. Consequently, there is a need for a scalable
+  nanostructured porous membrane.
+
+  Polymeric membranes based on self-assembling lyotropic liquid crystals (LLCs)
+  are suitable candidates for aqueous separation applications. LLCs are
+  amphiphilic molecules that share the characteristic ability of nanostructured
+  porous membrane materials to create highly ordered nanostructures with the
+  added benefits of low cost and synthetic techniques feasible for large-scale
   production \cite{feng_scalable_2014}. LLC systems created by the monomer
-  Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied
-  experimentally
+  Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied experimentally
   \cite{feng_scalable_2014,smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_thin_2016}.
-  Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h} phase
-  (Fig.\ref{fig:assembly}). The presence of ca. 10\% wt water results in the
-  H\textsubscript{II} phase. In both cases, monomers assemble into mesophases
-  made of hexagonally packed, uniform size, cylinders with hydrophilic head
-  groups oriented inward towards the cylinder center.  The hydrophilic region can
-  act as a pore for aqueous separations \cite{zhou_supported_2005}.  One can
-  envision tailoring the pore region for specific separations by changing the
-  monomer chemistry \cite{resel_h2-phase_2000}.
-
-  Research into LLC membranes has been revived in recent years. During early
+  The neat Na-GA3C11 monomer forms the thermotropic liquid crystalline (TLC)
+  Col\textsubscript{h} phase (Fig.\ref{fig:assembly}). The presence of ca. 10
+  wt\% added water results in formation of the lyotropic H\textsubscript{II}
+  phase. In both cases, Na-GA3C11 monomers assemble into mesophases made of
+  hexagonally packed, uniform size, cylinders with hydrophilic head groups
+  oriented inward towards the cylinder center. This LLC assembly is then
+  polymerized in situ to form a cross-linked polymer network to stabilize the
+  structure. The hydrophilic region can act as a pore for aqueous separations
+  \cite{zhou_supported_2005}.  One can envision tailoring the pore region for
+  specific separations by changing the monomer chemistry
+  \cite{resel_h2-phase_2000}.
+
+  Research into polymerized LLC membranes has been revived in recent years. During early
   stages of exploration, mesophases formed by Na-GA3C11 could not be
@@
 	\end{subfigure}
-	\caption{The liquid crystal monomer Na-GA3C11 (a) rendered atomistically (b)
+	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
 	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
@@
   precisely design membranes for specific separations. Over the past 20 years,
-  H\textsubscript{II} phase LLC membrane studies have been limited primarily to
-  Na-GA3C11 with some characterization done after minor structural modifications.
-  Resel et al.~varied the length of the monomer tails and the counterion used and
-  observed its affect on pore spacing \cite{resel_structural_2000}.  In a later
-  study of rejection performance, it was shown that membranes formed by Na-GA3C11
-  cannot perform separations of solutes less than 1.2 nm in diameter because the
-  pores are too large \cite{zhou_supported_2005}.  We do not yet understand how
-  to controllably reduce the effective pore size or how to tune the chemical
-  environment in the nanopores for effective water desalination and small organic
-  molecule separations. The only source of predictive modeling for LLC systems
-  have been macroscopic models which likely do not adequately describe transport
-  at these length scales \cite{hatakeyama_water_2011}. It will be challenging to
-  efficiently narrow down the large design space in a laboratory setting without
-  a robust model.
+  H\textsubscript{II}-phase LLC polymer membrane studies have been limited
+  primarily to Na-GA3C11 with some characterization done after minor structural
+  modifications.  Resel et al.~varied the length of the monomer tails and the
+  counterion used and observed its affect on pore spacing
+  \cite{resel_structural_2000}.  In a later study of rejection performance, it
+  was shown that membranes formed by cross-linked Na-GA3C11 in the
+  H\textsubscript{II} cannot perform separations of solutes less than 1.2 nm in
+  diameter because the pores are too large \cite{zhou_supported_2005}.  We do not
+  yet understand how to controllably reduce the effective pore size or how to
+  tune the chemical environment in the nanopores of this or related materials for
+  effective water desalination and small organic molecule separations. The only
+  source of predictive modeling for LLC systems have been macroscopic models that
+  likely do not adequately describe transport at these length scales
+  \cite{hatakeyama_water_2011}. It will be challenging to efficiently narrow down
+  the large design space in a laboratory setting without a robust model.
 
@@
   information as possible. We are most interested in reproducing the conclusions
-  about structure which have been drawn from X-ray diffraction (XRD) experiments
-  and in matching ionic conductivity measurements \cite{feng_thin_2016}.
-
-  A molecular level understanding of LLC membrane structure, enabled by
+  about structure which have been drawn from small angle X-ray scattering (SAXS)
+  and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
+  conductivity measurements \cite{feng_thin_2016}.
+
+  A molecular-level understanding of LLC polymer membrane structure, enabled by
   molecular dynamics simulations, can provide guidelines to reduce the large
@@
   (Fig. \ref{fig:detail}), assuming the force fields are sufficiently accurate.
-  With such an atomistic model, we can directly observe solute transport and
-  suggest governing mechanisms. We can observe how the choice of head group may
-  influence pore size for size exclusion driven separations. We can interchange
-  counterions which may influence both the pore size and the strength of the
-  Donnan potential which affects the degree to which the membrane can exclude
-  charged species.
+  With such an atomistic model, we can directly observe molecular-level solute
+  transport and suggest governing mechanisms. We can observe how the choice of
+  head group may influence pore size for size exclusion driven separations. We
+  can interchange counterions which may influence both the pore size and the
+  strength of the Donnan potential which affects the degree to which the membrane
+  can exclude charged species.
 
@@
 	   about transport behavior in the pore. A detailed molecular model (b) will allow us to
-	   directly observe solute transport. Here, four stacked layers of 5 monomers
+	   directly observe solute transport. Here, four stacked layers of 5 NA-GA3C11 monomers
            are pictured from atomistic simulations. The hydrophilic region is in red and the 
@@
   %necessary to put somewhere, but maybe not in this spot exactly
-  In order to appropriately model transport, we must first gain a thorough
-  understanding of the nanoscopic structure of LLC membranes. Our approach to
-  constructing a general model will follow the development of a model of the
-  assembly formed by Na-GA3C11 since it has sufficient experimental
-  characterization. We have also narrowed our scope to the development of a model
-  of the Col\textsubscript{h} phase membrane. Compared to the H\textsubscript{II}
-  phase, the Col\textsubscript{h} phase is a simpler starting point, due to the
-  absence of water, and has detailed experimental wide-angle X-ray scattering
-  (WAXS) patterns useful for reconstructing structural data. The two
-  phases appear to share similar structural characteristics since the pore 
-  spacings in each system are in close agreement \cite{feng_thin_2016,resel_structural_2000}.
+  In order to appropriately model transport in these ordered, nanoporous
+  organic systems, we must first gain a thorough understanding of the nanoscopic
+  structure of LLC polymer membranes. Our approach to constructing a general
+  model will follow the development of a model of the assembly formed by
+  Na-GA3C11 since it has sufficient experimental characterization. We have also
+  narrowed our scope to the development of a model of the Col\textsubscript{h}
+  phase membrane. Compared to the H\textsubscript{II} phase, the
+  Col\textsubscript{h} phase is a simpler starting point, due to the absence of
+  water, and has detailed experimental wide-angle X-ray scattering (WAXS)
+  patterns useful for reconstructing structural data. The two phases appear to
+  share similar structural characteristics since the pore spacings in each system
+  are in close agreement \cite{feng_thin_2016,resel_structural_2000}.
 
@@
   There remains the possibility that there is more than one metastable state
-  associated with a given LLC system. Simulating a membrane atomistically
+  associated with a given LLC phase. Simulating a membrane atomistically
   requires many atoms which limits the timescales acessible with MD. It is
@@
 
-  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
+  \item What constitutes a pore, and how well-defined are the pore regions? \label{point:poredefinition}
 

### 2018-01-02 Ben_Manuscripts/structure_paper/Draft.tex
Added some extra subsection headings based on Rich's feedback. They'll need editing

@@
 
-  \subsection{Determining the Spatial Configuration of Monomers}
+  \subsection{Determining the Number of Monomers per Layer}
 
@@
 
+  \subsection{Determining Definition of Layers}
+
   We learned that layers are well-defined and persistent, answering
@@
   \end{figure}
+
+  \subsection{Determination of Relative Interlayer Head Group Orientation}
 
@@
 
-  \subsection{Pore Structure Depends on Initial Configuration}
+  \subsection{Pore Structure Depends on Initial Configuration}  % Addresses pore definition
 

### 2018-01-03 Ben_Manuscripts/structure_paper/supplemental.tex
Beefing up supplemental info

@@
   \maketitle
+
+  \begingroup
+	\fontsize{14pt}{12pt}\selectfont
+	\textbf{Further details regarding monomer parameterization}
+  \endgroup
+
+  Monomers were parameterized according to the following procedure:
+  %BJC: need references
+  \begin{enumerate}
+	\item Create monomer structure file with connectivity : We drew atomistic
+        structures using MarvinSketch 17.13. We optimized the 3D geometry of
+	the structure using the 'Clean in 3D' function of MarvinSketch 17.13. 
+        We saved the structure as a .mol file, then converted it to .pdb
+	format using Open Babel 2.4.1. 
+	\item Assign GAFF atomtypes using \texttt{antechamber} : Using the .pdb
+	structure file as input, we ran \texttt{antechamber} using the AM1-BCC charge
+	model. The net charge on the monomer is input as -1 since the sodium ion will
+	be kept as a separate residue. The output of \texttt{antechamber} is used to
+	create Amber topology files with \texttt{LEaP}. A detailed tutorial can be
+	accessed elsewhere (http://ambermd.org/tutorials/basic/tutorial4b/) 
+	\item Create gromacs topologies from Amber output : \texttt{LEaP}
+	outputs a .inpcrd and a .prmtop file which are Amber topologies. Using
+	acpype.py, we convert the \texttt{LEaP} output into GROMACS .gro and .top
+	files. 
+  \end{enumerate}
 
@@
 
-  \textbf{TODO} : These are things I am working on / need to do
-
-  \begin{itemize}
-  \item Initial configuration dependence
-	\begin{itemize}
-		\item Initial pore-to-pore spacing
-		\item Initial pore radius
-		\item I have simulations running to support the claims that
-		these are not significant factors if chosen within reason. And
-		I will define what is meant by 'within reason'.
-	\end{itemize}
-  \item Description of parameterization process
-  \item Feel free to suggest anything else that might be useful
-  \end{itemize}
-
   \textbf{Calculation of pore-to-pore spacing statistics}
@@
   \begin{itemize}
-  \item We are interested in 5 pore-to-pore distances which should all be equal
-  in a perfect hexagonal array, however only 4 distances are independent % can
-  visualize this in supplemental material. Will make a lot of things more clear
-  below.
-  \item Each pore spacing has its own trajectory of spacing vs. time. Using
-  data collected after the system is equilibrated, we calculate how long it takes
-  for the data in each of the 5 trajetories to become uncorrelated using
+  	\item We are interested in 5 pore-to-pore distances which should all
+	be equal in a perfect hexagonal array, however only 4 distances are independent
+	% can visualize this in supplemental material. Will make a lot of things more
+	clear below.
+	\item Each pore spacing has its own trajectory of spacing vs. time.
+	Using data collected after the system is equilibrated, we calculate how long it
+	takes for the data in each of the 5 trajetories to become uncorrelated using
 	pymbar.timeseries.integratedAutocorrelationTime() % reference
-  \item We break the full trajectories down into sub-trajectories based on the
-  maximum autocorrelation time of those found in the previous step.
-  \item For each bootstrap trial, we recreate an equilibrium trajectory by
-  randomly sampling pore spacings from the sub-trajectories 
-  \item We get an average value for each pore spacing by finding the mean of
-  the bootstrapped data
-  \item We calculate the overall average as the mean of all bootstrapped pore
-  spacings
-  \item The uncertainty for each pore spacing is calculated as $\dfrac{<x> -
-  x}{4}$ where $<x>$ is the average spacing from the bootstrap trial and $x$ is
-  the average value of one of the pore spacings.
+	\item We break the full trajectories down into sub-trajectories based
+	on the maximum autocorrelation time of those found in the previous step.
+	\item For each bootstrap trial, we recreate an equilibrium trajectory
+	by randomly sampling pore spacings from the sub-trajectories 
+	\item We get an average value for each pore spacing by finding the
+	mean of the bootstrapped data
+	\item We calculate the overall average as the mean of all
+	bootstrapped pore spacings
+	\item The uncertainty for each pore spacing is calculated as
+	$\dfrac{<x> - x}{4}$ where $<x>$ is the average spacing from the bootstrap
+	trial and $x$ is the average value of one of the pore spacings.
 	\item We report the mean of these uncertainties
   \end{itemize}
+
+  \begingroup
+	\fontsize{14pt}{12pt}\selectfont
+	\textbf{Initial Configuration Dependence}
+  \endgroup
+
+  Any major dependence on initial configuration is addressed in the main text.
+  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
+  monomers per layer. We also showed that systems are stable when monomer head
+  groups are oriented in the parallel displaced and sandwiched configurations
+  (See Figure~\ref{fig:stacking}). Our model best supports a system built with 5
+  monomers per layer in the sandwiched configuration.
+
+  There are three other parameters whose choice may influence the equilibrium
+  structure: initial pore spacing, initial pore radius and initial distance
+  between layers. Here we show the results of a sensitivity analysis performed
+  on the three parameters. To reduce the size of the sensitivity analysis, we
+  only tested systems built with 5 monomers per layer with layers stacked in 
+  the parallel displaced configuration. All systems were equilibrated according
+  to the dry equilibration procedure.
+
+  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.
+
+  \begin{enumerate}
+
+	  \item \underline{Initial pore spacing}
+
+	  We tested five different initial pore spacings, defined as the
+	  distance between the central axis of each pore with all others. To reduce the
+	  number of variables, we held the pore radius constant, at 5 \AA~and the
+	  distance between layers at 3.7 \AA~since those were the values used in our
+	  optimal system in the main text. If the initial pore spacing is chosen to be
+	  too small, pore columns abruptly repel each other as soon as they are able to
+	  overcome the restraining potential present as part of the dry equilibration
+	  procedure. We avoided using systems that exhibit this behavior since the
+	  behavior increases the chances of a system to become kinetically trapped in an
+	  undesired metastable free energy basin.
+
+	  \begin{enumerate}
+
+	  	\item 39 \AA~: A pore spacing of 39 \AA~is used in order to have a test system
+		started with a spacing below the experimental value. As soon as the restraining
+		potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the columns are able to
+		separate resulting in a large jump in pore spacing (Figure~\ref{fig:p2p_39}).
+
+		\item 41 \AA~: A pore spacing of 41 \AA~is chosen since it closely matches the
+		experimental pore spacing.  Again, we observe abrupt repulsion of columns once
+		the restraining potential is switched to 56 KJ mol$^{-1}$ nm$^{-2}$
+		(Figure~\ref{fig:p2p_41}).
+
+		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger than the
+		experimental value. We observe relatively stable pore spacing during the
+		restrained portion of the dry equilibration procedure
+		(Figure~\ref{fig:p2p_45}). We chose to use this value for all our simulations
+		in the main text.
+
+		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \% larger than the
+		experimental value. Once the restraining potential reaches 56 KJ mol$^{-1}$
+		nm$^{-2}$, the pore spacing begins to decrease linearly (Figure~\ref{fig:p2p_50}).
+
+		\item 55 \AA~: We tested a pore spacing of 55 \AA~ which is at
+		a distance where monomers in each pore no longer intersect adjacent pores. Once
+		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
+		changes erratically until it begins to settle once the force constants are
+		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
+		avoiding a system such as this where vacuum gaps are introduced unnecessarily.
+
+	  \end{enumerate}
+
+	  %BJC: Could put vertical lines to indicate where position restraint values are reduced
+  	  \begin{figure}[htp]
+		\centering
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_39.png}\quad
+			\vspace{-1.25em}
+			\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
+		\end{subfigure}
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_41.png}\quad
+			\vspace{-1.25em}
+			\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
+		\end{subfigure}
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_45.png}
+			\vspace{-1.25em}
+			\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
+		\end{subfigure}
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_50.png}\quad	
+			\vspace{-1.25em}
+			\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
+		\end{subfigure}
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_55.png}
+			\vspace{-1.25em}
+			\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
+		\end{subfigure}
+
+		\caption{The pore spacing during the restrained portion of the
+			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
+			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 KJ
+			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
+			experimental value (a) or at the experimental value (b), there is an abrupt
+			change in pore spacing when the position restraints are reduced to 56 KJ
+			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA apart (c) the pore spacing
+			remains relatively stable. When pores are spaced 50 \AA apart (d), the pore
+			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
+			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA apart (e), so that monomers
+			do not intersect with adjacent pores, and position restraints are reduced to 56
+			KJ mol$^{-1}$ nm$^{-2}$, pore spacing changes erratically before stabilizing
+			when force constants are reduced to 3 KJ mol$^{-1}$ nm$^{-2}$.} 
+		\label{fig:p2p}
+	  \end{figure}
+
+	  \item \underline{Initial pore radius}
+
+	  We tested 3 different pore radii, defined as shown in
+	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
+	  pore spacing constant at 45 \AA~ and the distance between layers constant at
+	  3.7 \AA. Equilibrated values of pore radii are presented in
+	  Table~\ref{table:radii}. The pore radius in each frame is calculated as the
+	  average distance of all carbonyl carbons (See
+	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
+	  Statistics for the pore radii reported were generated from the timeseries
+	  representing the average pore radius at each frame.  Equilibration was detected
+	  using \texttt{pymbar.timeseries.detectEquilibration}. The average and standard
+	  deviation of pore radii were calculated using only data points collected after
+	  equilibration was detected.
+
+	  \begin{enumerate}
+
+		\item 2.5 \AA~: The smallest pore radius that we can achieve before energy 
+		minimization becomes problematic is 2.5 \AA.
+
+		\item 5 \AA~:
+
+		\item 8 \AA~: The largest pore radius that can achieve before energy minimization
+		becomes problematic is 8 \AA.
+	  \end{enumerate}
+
+	  \begin{table}[h]
+	  \centering
+	  \begin{tabular}{cc}
+	  \toprule
+	  Initial Pore Radius & Equilibrated Pore Radius \\
+	  \midrule
+	  % BJC: to be updated once simulations are run out long enough
+	  2.5 \AA & $0.394 \pm 0.002$ \AA \\
+	  5 \AA   & $0.423 \pm 0.002$ \AA \\ % final result
+	  8 \AA   & $0.721 \pm 0.002$ \AA \\
+	  \bottomrule
+	  \end{tabular}
+	  \caption{Caption of the future!}~\label{table:radii}
+	  \end{table}
+
+	  \item Initial distance between layers
+
+          We tested 3 different initial layer spacings, defined as the distance between the planes of 
+          aromatic rings in each layer. Systems built with layers stacked 3.7 \AA and 5 \AA apart
+	  are discussed extensively in the main text. We will focus the discussion here on systems
+	  built with layers stacked 10 \AA apart.
+
+  \end{enumerate}
 

### 2018-01-03 HII/Scripts/poresize.py

@@ -137,8 +137,8 @@ if __name__ == "__main__":
 
     t = md.load(args.traj, top=args.gro)  # load gromacs trajectory
     keep = [a.index for a in t.topology.atoms if a.name in args.components]   # get the index of all atoms in components
-    pore_components = t.atom_slice(keep)  # create a new trajectory object only describing those atoms
-    pos = pore_components.xyz
+    # pore_components = t.atom_slice(keep)  # create a new trajectory object only describing those atoms
+    pos = t.xyz[:, keep, :]
 
     pcenters = physical.avg_pore_loc(4, pos)  # find the pore centers
 
@@ -153,7 +153,7 @@ if __name__ == "__main__":
         order /= max(order)
 
     print('Pore size equilibrated after %d ns' % (old_div(t.time[poresize_equil], 1000)))
-    print('Average Pore Size: %.2f +/- %.2f nm' %(np.mean(r[poresize_equil:]), np.mean(r_std[poresize_equil:])))
+    print('Average Pore Size: %.3f +/- %.3f nm' %(np.mean(r[poresize_equil:]), np.std(r[poresize_equil:])))
     print('Order parameter equilibrated after %d ns' % (old_div(t.time[order_equil], 1000)))
     if args.normalize:
         print('Average Order Parameter: %.2f' % np.mean(order[order_equil:]))

### 2018-01-04 Ben_Manuscripts/structure_paper/Draft.tex
Removed passive voice unless it made sense to keep it

@@
   thereby permitting the design of solute-specific separation membranes
-  \cite{humplik_nanostructured_2011}. Most membrane-based aqueous separations of
-  small molecules can be achieved using reverse osmosis (RO) or nanofiltration
+  \cite{humplik_nanostructured_2011}. One can acheive most membrane-based aqueous separations of
+  small molecules using reverse osmosis (RO) or nanofiltration
   (NF) \cite{van_der_bruggen_review_2003}. While RO and NF have seen many
@@
   an undesired species \cite{werber_materials_2016}.
-
-  %MRS4: are all commercial RO membranes just like this? This seems
-  %awfully specific. 
-  %BJC3: Yea, pretty much all commercial membranes are TFC polyamide
-  % but I edited it to make it less specific.
 
@@
   process.  The most widely used phase-inversion process is immersion
-  precipitation, during which a polymer dissolved in a solvent is submerged in a
-  non-solvent. A solid, porous polymer membrane is all that remains once all
+  precipitation, during which one submerges a polymer, dissolved in a solvent, in
+  a non-solvent. A solid, porous polymer membrane is all that remains once all
   solvent has been removed by non-solvent exchange
@@
 
-  Research into polymerized LLC membranes has been revived in recent years. During early
-  stages of exploration, mesophases formed by Na-GA3C11 could not be
+  Research into polymerized LLC membranes has been revived in recent years.
+  During early stages of exploration, mesophases formed by Na-GA3C11 could not be
   macroscopically aligned, resulting in low flux membranes, and no clear route
   towards scalable and economical filtration. In 2014, Feng et al.~showed that
-  the mesophases could be aligned using a magnetic field with subsequent
+  one can align the mesophases using a magnetic field with subsequent
   crosslinking to lock the structure in place \cite{feng_scalable_2014}. In 2016,
-  Feng et al. showed that the same result could be obtained using a second technique
-  termed soft confinement \cite{feng_thin_2016}.
+  Feng et al. showed that one could obtain the same result using a second
+  technique termed soft confinement \cite{feng_thin_2016}.
 
@@
   information as possible. We are most interested in reproducing the conclusions
-  about structure which have been drawn from small angle X-ray scattering (SAXS)
+  about structure drawn from small angle X-ray scattering (SAXS)
   and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
@@
   A separate calculation based on the volume of the liquid crystal monomers
-  proposes that there are seven monomers in each layer
+  proposes that each layer consists of seven monomers
   \cite{resel_structural_2000}.  A molecular model orders of magnitude larger
@@
 
-  Experimentally, their existence is supported by evidence of strong $\pi$-$\pi$
-  stacking interactions in the direction perpendicular to the membrane plane.
-  $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups
-  which leaves no description of what is happening in the monomer tail region.
-  The tails may entangle isotropically while stacking order is maintained among
-  headgroups.
+  Strong $\pi$-$\pi$ stacking interactions in the direction perpendicular to
+  the membrane plane support the existence of layers experimentally.  $\pi$-$\pi$
+  stacking will only occur between the aromatic monomer head groups which leaves
+  no description of what is happening in the monomer tail region.  The tails may
+  entangle isotropically while maintaing stacking order among headgroups.
 
@@
 
-  While the Col\textsubscript{h} phase is described as dry, it has been
-  suggested by experimentalists, in unpublished communications, that it is likely
-  that small amounts of ambient water are leached into neat monomer.
-  Experimentally, achieving a hexagonal phase with a completely dry system has
-  proven difficult. If neat monomer is allowed to sit in ambient conditions, its
-  color turns from transparent to slightly opaque and a hexagonal phase forms.
-  Although we will not explore whether water is necessary for self-assembly, we
-  hypothesize that the hydrogen bonding network formed by the water may play a
-  role in structuring the pores and holding together the hexagonal phase. We can
-  use simulated X-ray diffraction patterns to see if there is any meaningful
-  structural difference between a ``dry'' and ``wet'' system.
+  While past work describes the Col\textsubscript{h} phase as dry
+  ~\cite{feng_scalable_2014}, it has been suggested by experimentalists, in
+  unpublished communications, that it is likely that neat monomer leaches small
+  amounts of ambient water.  Experimentally, achieving a hexagonal phase with a
+  completely dry system has proven difficult. If neat monomer sits in ambient
+  conditions, its color turns from transparent to slightly opaque and a hexagonal
+  phase forms.  Although we will not explore whether water is necessary for
+  self-assembly, we hypothesize that the hydrogen bonding network formed by the
+  water may play a role in structuring the pores and holding together the
+  hexagonal phase. We can use simulated X-ray diffraction patterns to see if
+  there is any meaningful structural difference between a ``dry'' and ``wet''
+  system.
 
@@
 
-  	\item The first is located at $q_z$ = 1.7 \angstrom$^{-1}$, corresponding to
-	a real space separation of 3.7 \angstrom~.  The reflection is attributed to
-	$\pi$-$\pi$ stacking between aromatic rings in the direction perpendicular to
-	the membrane plane, or z-axis \cite{feng_scalable_2014}. For simplicity, this
-	reflection will be referred to as R-$\pi$.
-
-	\item A weak intensity line is located at exactly half the $q_z$ value
-	of R-$\pi$ ($q_z$ = 0.85 \angstrom$^{-1}$), corresponding to a real space
-	periodic spacing of 7.4 \angstrom~. This reflection has been interpreted as
+	\item The location of the first is at $q_z$ = 1.7 \angstrom$^{-1}$,
+	corresponding to a real space separation of 3.7 \angstrom~. Previous
+	work~\ref{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
+	stacking between aromatic rings in the direction perpendicular to the membrane
+	plane, or z-axis \cite{feng_scalable_2014}. For simplicity, we will refer to
+	this reflection as R-$\pi$.
+
+	\item A weak intensity line, located at exactly half the $q_z$ value of
+	R-$\pi$ ($q_z$ = 0.85 \angstrom$^{-1}$), corresponds to a real space periodic
+	spacing of 7.4 \angstrom~. This reflection has been interpreted as
 	2\textsubscript{1} helical ordering of aromatic rings along the z axis
-	\cite{feng_scalable_2014}, meaning that if the positions of the aromatic rings
-	can be traced by a helix, then for each full turn in the helix, one will
-	encounter two aromatic rings. For this reason it will be referred to as
-	R-helix.
-
-	\item A third major reflection is marked by a low intensity ring
-	located at r = 1.4 \angstrom$^{-1}$. The real space separation corresponds to
-	4.5 \angstrom~ which is characteristic of the average spacing between packed
-	alkane chains \cite{mcintosh_organization_1980}. This reflection will be called
+	\cite{feng_scalable_2014}, meaning that if one traces the positions of the
+	aromatic rings with a helical curve, then for each full turn in the helix, one
+	will encounter two aromatic rings. For this reason we will refer to reflection
+	as R-helix.
+
+	\item A low intensity ring located at r = 1.4 \angstrom$^{-1}$ marks
+	the third major reflection of interest. The real space separation corresponds
+	to 4.5 \angstrom~ which is characteristic of the average spacing between packed
+	alkane chains \cite{mcintosh_organization_1980}. We will call this reflection
 	R-alkanes.
 
-	\item Within R-alkanes, are four spots of higher relative intensity
-	which will be called R-spots. All are located $\sim 37$ degrees from the $q_z$
-	axis in their respective quadrants. In many liquid crystal systems this can be
-	explained by the tilt angle of the alkane chains with respect to the membrane
-	plane \cite{govind_simple_2001}.
+	\item Within R-alkanes, are four spots of higher relative intensity.
+	Accordingly, we name these reflection R-spots. Thin location of all spots is $\sim 37$
+	degrees from the $q_z$ axis in their respective quadrants. In many liquid
+	crystal systems one can explain the spots by the tilt angle of the alkane chains
+	with respect to the membrane plane \cite{govind_simple_2001}.
 
 	\item The final feature corresponds to the spacing and symmetry of the
-	d\textsubscript{100} plane which can be related to the distance between pores.
-	The feature, which will be called R-pores, is characterized by dots along $q_z$
-	= 0. The spacing between dots is indicative of the hexagonal symmetry of the
-	packed pores. The same information at higher resolution is obtained using SAXS (Fig.~\ref{fig:SAXS}).
+	d\textsubscript{100} plane. This plane is geometrically related the distance
+	between pores.  The feature, which we named R-pores, is characterized by dots
+	along the equatorial axis defined when $q_z$ = 0. The spacing between dots is
+	indicative of the hexagonal symmetry of the packed pores. We observe the same
+	information at higher resolution using SAXS (Fig.~\ref{fig:SAXS}).
 
@@
 		Monomer tails tilt with respect to the membrane plane. (V) As derived from
-		SAXS, pores pack hexagonally and are spaced 4.12 nm apart}
+		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
 	\label{fig:SWAXS}
@@
 
-  Liquid crystal monomers were parameterized using the Generalized AMBER
+  We parameterized the liquid crystal monomers using the Generalized AMBER
   Forcefield \cite{wang_development_2004} with the Antechamber package
   \cite{wang_automatic_2006} provided with AmberTools16
-  \cite{case_ambertools16_2016}. Atomic charges were assigned using the am1bccsym
+  \cite{case_ambertools16_2016}. We assigned atomic charges using the am1bccsym
   method of \texttt{molcharge} shipped with QUACPAC from Openeye Scientific
-  Software. All molecular dynamics simulations were run using Gromacs 2016
+  Software. We ran all molecular dynamics simulations using Gromacs 2016
   \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
-  An ensemble of characteristic, low-energy vacuum monomer
-  configurations were constructed by applying a simulated annealing process to a
-  parameterized monomer. Monomers were cooled from 1000K to 50K over 10
-  nanoseconds.  A low energy configuration was randomly pulled from the
-  trajectory and charges were reassigned using \texttt{molcharge}.  Using the new
-  charges, the monomer system was annealed again and a random monomer
-  configuration was pulled from the trajectory to be used for full system
+
+  We constructed an ensemble of characteristic, low-energy vacuum monomer
+  configurations by applying a simulated annealing process to a
+  parameterized monomer. We cooled monomers from 1000K to 50K over 10
+  nanoseconds. We randomly pulled a low energy configuration from the
+  trajectory then reassigned charges using \texttt{molcharge}. Using the new
+  charges, we annealed the monomer system again and pulled a random monomer
+  configuration the trajectory which we used for full system
   construction (Figure~\ref{fig:python}a). See supplemental information for
@@
   indicators of progress towards an ordered system. To bypass the slow
-  self-assembly process, Python scripts are used to assemble monomers into a
+  self-assembly process, we use Python scripts to assemble monomers into a
   structure close to one of a number of hypothesized equilibrium configurations
@@
 	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
-	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
-		configuration. (b) Monomers are rotated and assembled into layers with 
-		hydrophilic centers. (c) Twenty layers are stacked on top of each other to create
-		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
+	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
+		configuration. (b) Python scripts rotate and assemble monomers into layers with 
+		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
+		pores. (d) The pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
   \end{figure}
@@
   continuity along the pore axis, avoiding any edge effects and creating an
-  infinite length pore ideal for studying transport. A small number of layers is
-  preferred in order to reduce computational cost and to allow us to look at
+  infinite length pore ideal for studying transport. We prefer a small number of layers
+  in order to reduce computational cost and to allow us to look at
   longer timescales. Ultimately, we chose to build a system with 20 monomer
@@
   pore radius, defined as the distance of a chosen head group carbon from the
-  pore's central axis, does not influence the equilibrium structure when a
-  reasonable value is chosen (See Supplemental Information). The pore radius is
-  chosen to be 0.6 nm in our initial configurations because the pore size is
-  estimated to be $\sim$1.2 nm \cite{zhou_supported_2005}. The initial distance
-  between pores also has little effect on the the equilibrated structure (See
-  supplemental information). However, one should not start them too close or
-  there will be high energy repulsions during early equilibration. We chose an
-  initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
-  of 4.12 nm.  The distance between layers, the rotation of the layers with
-  respect to adjacent layers, and the number of monomers per layer do influence
-  the equilibrium structure and require further justification for their choices.
-  We rely on experimental data to inform them.
+  pore's central axis, does not influence the equilibrium structure if one choses
+  a reasonable value (See Supplemental Information). The pore radius is chosen to
+  be 0.6 nm in our initial configurations because the pore size is estimated to
+  be $\sim$1.2 nm \cite{zhou_supported_2005}. The initial distance between pores
+  also has little effect on the the equilibrated structure (See supplemental
+  information). However, one should not start them too close or there will be
+  high energy repulsions during early equilibration. We chose an initial pore
+  spacing of 4.5 nm, $\sim$10\% larger than the experimental value of 4.12 nm.
+  The distance between layers, the rotation of the layers with respect to
+  adjacent layers, and the number of monomers per layer do influence the
+  equilibrium structure and require further justification for their choices.  We
+  rely on experimental data to inform them.
 
@@
   plane. We explore two different initial layer spacings. The first is exactly
-  equal to R-$\pi$ with layers placed so aromatic rings are stacked 3.7
-  \angstrom~apart in the z-direction. A second system is explored with an initial
-  layer spacing of 5 \angstrom. A third system with an initial layer spacing of
-  10 \angstrom~was briefly explored. When layers are spaced out too far, they
-  will collapse on each other while simultaneously slipping in between layers of
-  adjacent pores, which leads to an artificially thick membrane with pores spaced
-  closely together.  Further details of simulations with large layer spacing are
-  in the supplemental information.
-
-  The relative interlayer orientation was chosen based on clues from
-  diffraction data as well as the various known stacking modes of benzene and
-  substituted benzene rings: sandwiched, parallel-displaced and T-shaped
-  \cite{sinnokrot_estimates_2002} (Fig. \ref{fig:sandwiched} and \ref{fig:pd,fig:tshaped}).
-  The T-shaped configuration was ruled out because its $\sim$5 \angstrom~
-  equilibrium stacking distance \cite{sinnokrot_estimates_2002} is inconsistent
-  with R-$\pi$. It is also infeasible for the monomers to orient in the T-shaped
-  conformation because of the bulky tail groups. The system's preference towards
-  the sandwiched vs. parallel displaced stacking modes will be explored in some
-  detail. Both have reported stacking distances near the R-$\pi$ value of 3.7
-  \angstrom. Headgroups in our sandwiched initial configuration are stacked
-  directly on top of each other while stacked headgroups in the parallel
-  displaced initial configuration are offset by $180/nmon$ degrees where $nmon$
-  equals the number of monomers per layer.
+  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
+  the z-direction. We explore a second system with an initial layer spacing of 5
+  \AA. We briefly explored a third system with an initial layer spacing of 10
+  \AA. If we initially space layers too far apart, they will collapse on each
+  other while simultaneously slipping in between layers of adjacent pores, which
+  leads to an artificially thick membrane with pores spaced closely together.
+  Further details of simulations with large layer spacing are in the supplemental
+  information.
+
+  We chose the relative interlayer orientation based on clues from diffraction
+  data as well as the various known stacking modes of benzene and substituted
+  benzene rings: sandwiched, parallel-displaced and T-shaped
+  \cite{sinnokrot_estimates_2002} (Fig. \ref{fig:sandwiched} and
+  \ref{fig:pd,fig:tshaped}).  We ruled out the T-shaped configuration because its
+  $\sim$5 \angstrom~ equilibrium stacking distance
+  \cite{sinnokrot_estimates_2002} is inconsistent with R-$\pi$. It is also
+  infeasible for the monomers to orient in the T-shaped conformation because of
+  the bulky tail groups. We will explore the system's preference towards the
+  sandwiched vs. parallel displaced stacking modes in some detail. Both have
+  reported stacking distances near the R-$\pi$ value of 3.7 \angstrom. Headgroups
+  in our sandwiched initial configuration stack directly on top of each other
+  while headgroups in the parallel displaced initial configuration stack
+  with an offset of $180/nmon$ degrees where $nmon$ equals the number of monomers
+  per layer.
 
@@
   (\ref{point:monomernum}). We tested configurations constructed with a varied
-  number of monomers per layer. Systems were built in the offset and parallel
+  number of monomers per layer. We built systems in the offset and parallel
   displaced configurations with 4, 5, 6, 7 and 8 monomers per layer.
@@
   the square root of its previous value. Once the force constant is below 10 KJ
-  mol$^{-1}$ nm$^{-2}$, the restraints are reduced in a sequence with values of
-  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. The resulting
-  unrestrained structure is allowed to equilibrate for 5 ns in the NPT ensemble
+  mol$^{-1}$ nm$^{-2}$, the we reduce the restraints in a sequence with values of
+  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
+  unrestrained structure to equilibrate for 5 ns in the NPT ensemble
   with pressure controlled by the berendsen barostat. Next, we run long NPT
@@
   In order to create a wet system, we solvated an initial configuration with
-  water using \texttt{gmx solvate}. All water molecules placed outside the pore
-  region are removed. Waters inside the pore region are randomly removed until
-  the desired concentration of water in the pores is reached. The remainder of
-  the equilibration follows the same procedure as the dry system.
+  water using \texttt{gmx solvate}. We remove all water molecules placed outside
+  the pore region. Then we randomly remove water molecules inside the pore region
+  until the pores reach the desired concentration of water. The remainder of the
+  equilibration follows the same procedure as the dry system.
 
@@
   In order to fully match synthetic procedures, we created a crosslinking
-  algorithm that can be applied to equilibrated structures. The purpose of
+  algorithm that one can apply to equilibrated structures. The purpose of
   crosslinking is to maintain macroscopic alignment of the crystalline domains,
@@
   concerned with replicating the kinetics of the reaction, but instead emphasize
-  the consistency of the final structure with experimental structural data. The
-  algorithm was developed based on the known reaction mechanism. Crosslinking of
+  the consistency of the final structure with experimental structural data. We
+  developed the algorithm based on the known reaction mechanism. Crosslinking of
   this system is a free radical polymerization (FRP) taking place between
@@
   an initiator which bonds to the system, meaning new atoms are introduced into
-  the system. For simplicity, the initiator was simulated as hydrogen and made
+  the system. For simplicity, we simulated the initiator as hydrogen and made it
   present in the simulation by including them in all possible locations where an
-  addition could occur as dummy atoms. The crosslinking procedure is carried out
-  iteratively. During each iteration, bonding carbon atoms are chosen based on a
-  distance cut-off. The topology is updated with new bonds and dummy hydrogen
-  atoms are changed to appropriate hydrogen types. Head-to-tail addition was the
-  only propagation mode considered due to its dominance in the real system \cite{young_introduction_2011}.
-  Direction of attack was not considered because the resultant mixture is
-  racemic.
+  addition could occur as dummy atoms. We carry out the crosslinking procedure
+  iteratively. During each iteration, the algoritm selects eligible bonding
+  carbon atoms based on a distance cut-off. The topology is updated with new
+  bonds and dummy hydrogen atoms are changed to appropriate hydrogen types.
+  Head-to-tail addition was the only propagation mode considered due to its
+  dominance in the real system \cite{young_introduction_2011}. We did not
+  consider direction of attack because the resultant mixture is racemic.
 
@@
   To calculate the equilibrated pore spacing, we measured the distance between
-  pore centers. Pore centers are located by averaging the coordinates of sodium
-  ions in their respective pores. Pore spacing statistics were generated 
+  pore centers. We located the pore centers by averaging the coordinates of sodium
+  ions in their respective pores. We generated pore spacing statistics 
   using the bootstrapping technique (See Supplemental Information).
@@
 
-  The colorbars on all diffraction patterns are normalized relative to
+  We normalized the colorbars on all diffraction patterns relative to
   R-alkanes. We believe that the alkane-alkane density, averaged over all angles,
@@
   looked at the average number density of sodium ions, aromatic rings and carbon
-  atoms making up the monomer tails. The radial distance of all atoms in each
-  group from the pore centers are binned, then normalized by the volume of the
+  atoms making up the monomer tails. We binned the radial distance of all atoms
+  in each group from the pore centers, then normalized by the volume of the
   annulus defined by the bin edges and z box vector.
@@
   indicated by the Einstein relation \cite{einstein_investigations_1956}. We
-  visualized the MSD plot to determine where to begin and end a linear fit. Ion
-  concentration was measured with respect to the volume of the entire unit cell.
+  visualized the MSD plot to determine where to begin and end a linear fit. We
+  measured ion concentration with respect to the volume of the entire unit cell.
 
@@
   of charge of the system. The conductance, $\gamma$, of the system can be
-  calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic
-  conductivity is achieved by multiplying by channel length and dividing by the
+  calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$ We convert the resulting value
+  to ionic conductivity by multiplying by channel length and dividing by the
   membrane cross sectional area. $D_Q$ is the diffusion coefficient of the
-  collective variable Q. It can be calculated using the Einstein relation.  A
-  full derivation of the model can be accessed elsewhere 
-  \cite{liu_collective_2013}.
+  collective variable Q. It is calculated using the Einstein relation. One can
+  access a full derivation of the model elsewhere \cite{liu_collective_2013}.
 
@@
   the monomer layers, addressing (\ref{point:monomernum}), we ran simulations of
-  systems created with 4 - 8 monomers per layer. Systems were built in both the
+  systems created with 4 - 8 monomers per layer. We built systems in both the
   parallel displaced and sandwiched configurations with layers initially spaced
-  3.7 \AA~apart. Equilibrated configurations were prepared according to the dry
+  3.7 \AA~apart. We prepared equilibrated configurations according to the dry
   equilibration procedure. All systems are stable after 400 ns of simulation. In
@@
   with 5 monomers per layer in the parallel displaced and sandwiched
-  configurations. Simulated patterns were generated using portions of simulation
+  configurations. We generated simulated patterns using portions of simulation
   trajectory after equilibration. The patterns for both structures are shown and
@@
   The R-spots signal, which appears in both simulated XRD patterns, is a result
-  of hexagonal alkane chain packing. Previously, the spots in the diffraction
-  pattern had been explained as the product of tilted alkane chains. We measured
+  of hexagonal alkane chain packing. Previous literature has explained the spots
+  in the diffraction pattern as the product of tilted alkane chains. We measured
   the tilt angle of the alkane chains and showed that our system equilibrates to
@@
 	\end{subfigure}
-	\caption{(a) All atoms except carbon atoms making up the tails are removed from a 
+	\caption{(a) We removed all atoms except carbon atoms making up the tails from a 
 	sandwiched configuration trajectory. (b) The simulated diffraction pattern of the
@@
 %  to stack further apart than 3.7 \angstrom~as suggested by experiment.
-  When systems are built with layers stacked 5.0 \AA~apart then equilibrated,
-  we observe long-term stability of a qualitatively different configuration,
-  suggesting that we have found another metastable free energy basin, further
-  corroborating (\ref{point:metastable}). For reasons to become aparent later,
-  we will refer to this class of systems as the disordered pore basin. 
-  Systems with layers initially stacked 3.7 \AA~apart will be referred to
-  as the ordered basin. We studied each basin in both the parallel
+  When we build systems with layers stacked 5.0 \AA~apart and then let them
+  equilibrate, we observe long-term stability of a qualitatively different
+  configuration, suggesting that we have found another metastable free energy
+  basin, further corroborating (\ref{point:metastable}). For reasons to become
+  aparent later, we will refer to this class of systems as the disordered pore
+  basin.  Systems which we build with layers initially stacked 3.7 \AA~apart will
+  be referred to as the ordered basin. We studied each basin in both the parallel
   displaced and sandwiched configurations.
@@
   In the parallel displaced configuration, almost all contrast between R-spots
-  and R-alkanes is faded (Fig.~\ref{fig:offset_disordered_xrd}). In the
+  and R-alkanes fades (Fig.~\ref{fig:offset_disordered_xrd}). In the
   sandwiched configuration, R-spots is weakly present, but in different
@@
   used only carbon atoms of the monomer tails (See Supplemental Information for
-  diagram). Histograms are averaged over at least 50 ns of equilibrated trajectory.
+  diagram). We average the histograms over at least 50 ns of equilibrated trajectory.
 
@@
   There is a partition between the hydrophobic and hydrophilic regions, however
-  it is a gradient in composition, rather than an abrupt division. Sodium ions
-  and head groups are not confined to just within the pore region. In all cases,
-  19\% of sodium ions exist outside the pore region whose radius is assumed to be
-  0.6 nm for this calculation (except sandwiched, ordered pore , where 16\% are
-  outside the pore). Additionally, we see that in all cases, about 3\% of the
+  it is a gradient in composition, rather than an abrupt division. The system
+  does not confine sodium ions and head groups to just within the pore region.
+  Assuming a pore radius of 0.6 nm, we see in all cases, that 19\% of sodium ions
+  exist outside the pore region (except sandwiched, ordered pore , where 16\%
+  are outside the pore). Additionally, we see that in all cases, about 3\% of the
   plotted tail density is located within the pore region (except sandwiched,
@@
   	\end{tabular}
-  	\caption{simulated diffraction patterns generated from trajectories of systems 
+  	\caption{Simulated diffraction patterns generated from trajectories of systems 
   	built in the parallel displaced and sandwiched configurations as a function
@@
   In all cases, water disrupts structuring of the model \ref{fig:solvation}.
-  The intensity of the reflections decrease when water is added to the system. In
+  When we add water to the system, the intensity of the reflections decrease. In
   systems built with 5 wt\% water, R-$\pi$ and R-spots become nearly
@@
 
-  The membrane swells when water is introduced. The location of maximum head
+  The membrane swells when we introduce water. The location of maximum head
   group density shifts from 0.35 to 0.62 nm and from 0.44 to 0.61 nm in the
-  parallel displaced and sandwiched configurations respectively. Again, we observe the
-  existence of ions, head groups and water outside the pore region, however in the
-  hydrated system, the head groups drift beyond 1.5 \AA~from the pore center. In
-  the dry systems, head groups did not wander beyond 1.4 \AA~from the pore
-  center. Both observations suggest that all components are pushed radially
-  outward from the pore center, characteristic of a swelling process.
+  parallel displaced and sandwiched configurations respectively. Again, we
+  observe the existence of ions, head groups and water outside the pore region,
+  however in the hydrated system, the head groups drift beyond 1.5 \AA~from the
+  pore center. In the dry systems, head groups did not wander beyond 1.4 \AA~from
+  the pore center. Both observations suggest that water pushes all components
+  radially outward from the pore center, characteristic of a swelling process.
 
@@
   gives reasonable estimates of ionic conductivity when compared to experiment.
-  Calculated values of ionic conductivity obtained using the Nernst-Einstein
-  relation and Collective Diffusion model are compared in
+  We compare calculated values of ionic conductivity obtained using the
+  Nernst-Einstein relation and Collective Diffusion model in
   Figure~\ref{fig:conductivity}. The two methods agree with each other within
   error, although the uncertainty obtained using the Collective Diffusion model
-  is much higher. Much longer simulations are needed to lower the uncertainty,
+  is much higher. We require much longer simulations to lower the uncertainty,
   however it is not feasible to do so with a large system. We will only use the
@@
   the real system studied experimentally. The ionic conductivity measurement to
-  which we are comparing was done on a \SI{80}{\micro\metre} thick film, nearly
+  which we are comparing was done with a \SI{80}{\micro\metre} thick film, nearly
   10,000 times thicker than our simulated system. The thick film is likely
@@
   parallel-displaced configuration built with 5 monomers per layer. We simulated
-  the crosslinked system in the NPT ensemble for 100 ns. The distance between
-  pores shrinks by 0.4 \angstrom~and the distance between layers increases by
-  0.04 \AA~after the system is crosslinked. All major features are still present
-  in the simulated XRD patterns, however at lower intensities
+  the cross-linked system in the NPT ensemble for 100 ns. After the system is
+  cross-linked, the distance between pores shrinks by 0.4 \AA~and the distance
+  between layers increases by 0.04 \AA. All major features are still present in
+  the simulated XRD patterns, however at lower intensities
   (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using the
@@
 	  the uncrosslinked system. (b) The ionic conductivity is smaller relative to the
-	  uncrosslinked system, but still much larger than the experimental value. (c)
-	  The distance between layers increases when the system is crosslinked. (d) The
-	  pore spacing decreases when the membrane is crosslinked.}~\label{fig:xlink}
+	  uncrosslinked system, but still much larger than the experimental value. When
+	  the system is cross-linked, The distance between layers increases (c) and the
+	  pore spacing decreases (d)}~\label{fig:xlink}
   \end{figure}
@@
 
-  We learned that water is not needed to create well-defined pore structures.
+  We learned that we do not need water to create well-defined pore structures.
   Systems whose pores were filled with varying amounts of water showed a decrease

### 2018-01-04 Ben_Manuscripts/structure_paper/Draft.tex
Minor edits

@@
   designing membranes at the molecular level. Next-generation nanoporous
-  membranes with high selectivity permitted by a precisely controlled pore size
-  and high permeability allowed by its porous architecture, have the potential to
+  membranes with high selectivity, permitted by a precisely controlled pore size,
+  and high permeability, allowed by its porous architecture, have the potential to
   replace traditional RO and NF membrane technologies.
@@
   wt\% added water results in formation of the lyotropic H\textsubscript{II}
-  phase. In both cases, Na-GA3C11 monomers assemble into mesophases made of
+  phase. In both cases, Na-GA3C11 monomers assembles into mesophases made of
   hexagonally packed, uniform size, cylinders with hydrophilic head groups
@@
   one can align the mesophases using a magnetic field with subsequent
-  crosslinking to lock the structure in place \cite{feng_scalable_2014}. In 2016,
+  cross-linking to lock the structure in place \cite{feng_scalable_2014}. In 2016,
   Feng et al. showed that one could obtain the same result using a second
@@
   was shown that membranes formed by cross-linked Na-GA3C11 in the
-  H\textsubscript{II} cannot perform separations of solutes less than 1.2 nm in
+  H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in
   diameter because the pores are too large \cite{zhou_supported_2005}. We do not
@@
 %  present in the real system
-  A separate calculation based on the volume of the liquid crystal monomers
-  proposes that each layer consists of seven monomers
-  \cite{resel_structural_2000}.  A molecular model orders of magnitude larger
-  than any other reported atomistic liquid crystal membrane simulations, as we
-  present here, has the best chance of directly answering this question.  We will
+  A separate calculation based on the estimated volume of the liquid crystal
+  monomers proposes that each layer consists of seven monomers
+  \cite{resel_structural_2000}. Our best chance to answer this question is by
+  using a molecular model orders of magnitude larger than any other reported
+  atomistic liquid crystal membrane simulation, as we present here. We will
   directly change the layer composition and note its effect on membrane
@@
   benzene dimers have shown a clear energetic advantage for parallel displaced
-  and T-shaped $\pi$-$\pi$ stacking conformations versus a sandwiched
+  and T-shaped $\pi$-$\pi$ stacking conformations over a sandwiched
   conformation \cite{sinnokrot_estimates_2002}. Substituted benzene rings
@@
 	\item Within R-alkanes, are four spots of higher relative intensity.
-	Accordingly, we name these reflection R-spots. Thin location of all spots is $\sim 37$
+	Accordingly, we name these reflection R-spots. The location of all spots is $\sim 37$
 	degrees from the $q_z$ axis in their respective quadrants. In many liquid
@@
 	indicative of the hexagonal symmetry of the packed pores. We observe the same
-	information at higher resolution using SAXS (Fig.~\ref{fig:SAXS}).
+	information with higher resolution using SAXS (Fig.~\ref{fig:SAXS}).
 
@@
 
-  We constructed an ensemble of characteristic, low-energy vacuum monomer
+  We generated an ensemble of characteristic, low-energy vacuum monomer
   configurations by applying a simulated annealing process to a
@@
   charges, we annealed the monomer system again and pulled a random monomer
-  configuration the trajectory which we used for full system
+  configuration from the trajectory which we used for full system
   construction (Figure~\ref{fig:python}a). See supplemental information for
@@
   rotated so the plane of the aromatic head groups would be coplanar with the xy
-  plane. We explore two different initial layer spacings. The first is exactly
+  plane. We explored three different initial layer spacings. The first is exactly
   equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
@@
   leads to an artificially thick membrane with pores spaced closely together.
-  Further details of simulations with large layer spacing are in the supplemental
+  Further details of simulations with layer stacked 10 \AA apart are in the supplemental
   information.
@@
   the square root of its previous value. Once the force constant is below 10 KJ
-  mol$^{-1}$ nm$^{-2}$, the we reduce the restraints in a sequence with values of
+  mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
   8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
@@
 
-  \subsection{Crosslinking}
-
-  In order to fully match synthetic procedures, we created a crosslinking
+  \subsection{Cross-linking}
+
+  In order to fully match synthetic procedures, we created a cross-linking
   algorithm that one can apply to equilibrated structures. The purpose of
-  crosslinking is to maintain macroscopic alignment of the crystalline domains,
+  cross-linking is to maintain macroscopic alignment of the crystalline domains,
   ensuring aligned, hexagonally packed pores. For that reason, we are not
   concerned with replicating the kinetics of the reaction, but instead emphasize
-  the consistency of the final structure with experimental structural data. We
-  developed the algorithm based on the known reaction mechanism. Crosslinking of
-  this system is a free radical polymerization (FRP) taking place between
-  terminal vinyl groups present on each of the three monomer tails. FRPs require
-  an initiator which bonds to the system, meaning new atoms are introduced into
-  the system. For simplicity, we simulated the initiator as hydrogen and made it
-  present in the simulation by including them in all possible locations where an
-  addition could occur as dummy atoms. We carry out the crosslinking procedure
-  iteratively. During each iteration, the algoritm selects eligible bonding
-  carbon atoms based on a distance cut-off. The topology is updated with new
-  bonds and dummy hydrogen atoms are changed to appropriate hydrogen types.
-  Head-to-tail addition was the only propagation mode considered due to its
-  dominance in the real system \cite{young_introduction_2011}. We did not
-  consider direction of attack because the resultant mixture is racemic.
-
-  Our implementation requires long simulation times to achieve high crosslink 
-  densities. A typical crosslinking procedure can take up to 24 hours. In
+  the consistency of the final structure with experimental structural data.
+
+  We developed the algorithm based on the known reaction mechanism.
+  Cross-linking of this system is a free radical polymerization (FRP) taking
+  place between terminal vinyl groups present on each of the three monomer tails.
+  FRPs require an initiator which bonds to the system, meaning new atoms are
+  introduced into the system. For simplicity, we simulated the initiator as
+  hydrogen and made it present in the simulation by including them as dummy atoms
+  in all possible locations where an addition could occur. We carry out the
+  cross-linking procedure iteratively. During each iteration, the algoritm
+  selects eligible bonding carbon atoms based on a distance cut-off. The topology
+  is updated with new bonds and dummy hydrogen atoms are changed to appropriate
+  hydrogen types.  Head-to-tail addition was the only propagation mode considered
+  due to its dominance in the real system \cite{young_introduction_2011}. We did
+  not consider direction of attack because the resultant mixture is racemic.
+
+  Our implementation requires long simulation times to achieve high cross-link 
+  densities. A typical cross-linking procedure can take up to 24 hours. In
   order to collect equilibrated data, further NPT simulation is necessary. We
-  typically run a crosslinked system for an additional 100 ns to allow the system
-  to readjust. For those reasons we did not crosslink all systems tested, but only
-  the most promising structure. We show that crosslinking does not significantly
+  typically run a cross-linked system for an additional 100 ns to allow the system
+  to readjust. For those reasons we did not cross-link all systems tested, but only
+  the most promising structure. We show that cross-linking does not significantly
   change any of our drawn conclusions in Section 3.6.
@@
   R-alkanes of the experimental pattern, $I_{avg}$. We exclude intensities
-  within $\pm$ 30\degree~of the $q_r=0$ axis, since the simulated patterns differ
+  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$ , since the simulated patterns differ
   from experiment in those regions. Specifically, in contrast to the
@@
   $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$ 
-  Sodium ion diffusion coefficients were found by calculating the slope
+  We measured sodium ion diffusion coefficients by calculating the slope
   of the linear region of the z-direction mean square displacement curve as
@@
   basin, further corroborating (\ref{point:metastable}). For reasons to become
-  aparent later, we will refer to this class of systems as the disordered pore
+  apparent later, we will refer to this class of systems as the disordered pore
   basin. Systems which we build with layers initially stacked 3.7 \AA~apart will
@@
   In all cases, the space in the pore region is filled with sodium ions and
-  head groups. In ordered pore systems, there is less density in the center of
+  head groups. In the ordered pore systems, there is less density in the center of
   the pore indicating a more ordered pore structure. In both the sandwich and
@@
   The system's structure and physical characteristics did not change
-  significantly when we applied the crosslinking algorithm to the equilibrated
+  significantly when we applied the cross-linking algorithm to the equilibrated
   parallel-displaced configuration built with 5 monomers per layer. We simulated
@@
   (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using the
-  Nernst-Einstein relation and found that it is lower in the crosslinked system
+  Nernst-Einstein relation and found that it is lower in the cross-linked system
   (Fig.~\ref{fig:IC_xlink}).
@@
   \end{subfigure}
-  \caption{(a) Reflections produced by the crosslinked configuration fade
-	  relative to the uncrosslinked system. The colorbar shown is the same used for
-	  the uncrosslinked system. (b) The ionic conductivity is smaller relative to the
-	  uncrosslinked system, but still much larger than the experimental value. When
+  \caption{(a) Reflections produced by the cross-linked configuration fade
+	  relative to the uncross-linked system. The colorbar shown is the same used for
+	  the uncross-linked system. (b) The ionic conductivity is smaller relative to the
+	  uncross-linked system, but still much larger than the experimental value. When
 	  the system is cross-linked, The distance between layers increases (c) and the
@@
   Finally, we verified that our conclusions do not change when the system is
-  crosslinked by the algorithm we implemented. The diffraction pattern weakens
-  relative to the uncrosslinked system, the ionic conductivity drops by a factor
+  cross-linked by the algorithm we implemented. The diffraction pattern weakens
+  relative to the uncross-linked system, the ionic conductivity drops by a factor
   of ca. 1.5, in closer agreement with experiment, the pore spacing decreases and

### 2018-01-05 Ben_Manuscripts/structure_paper/supplemental.tex
Minor edits to draft and additions to supplemental information

@@
 
+  \bibliographystyle{ieeetr}
   \graphicspath{{./figures/}}  % put all the figures here
@@
 
+  \noindent
   \begingroup
-	\fontsize{14pt}{12pt}\selectfont
+	\fontsize{14pt}{14pt}\selectfont
 	\textbf{Further details regarding monomer parameterization} 
@@
 
+  \vspace{1em}
   Monomers were parameterized according to the following procedure:
-  %BJC: need references
   \begin{enumerate}
-	\item Create monomer structure file with connectivity : We drew atomistic
-        structures using MarvinSketch 17.13. We optimized the 3D geometry of
-	the structure using the 'Clean in 3D' function of MarvinSketch 17.13. 
-        We saved the structure as a .mol file, then converted it to .pdb
-	format using Open Babel 2.4.1. 
-	\item Assign GAFF atomtypes using \texttt{antechamber} : Using the .pdb
-	structure file as input, we ran \texttt{antechamber} using the AM1-BCC charge
-	model. The net charge on the monomer is input as -1 since the sodium ion will
-	be kept as a separate residue. The output of \texttt{antechamber} is used to
-	create Amber topology files with \texttt{LEaP}. A detailed tutorial can be
-	accessed elsewhere (http://ambermd.org/tutorials/basic/tutorial4b/) 
-	\item Create gromacs topologies from Amber output : \texttt{LEaP}
-	outputs a .inpcrd and a .prmtop file which are Amber topologies. Using
-	acpype.py, we convert the \texttt{LEaP} output into GROMACS .gro and .top
-	files. 
+	\item \textit{Create monomer structure file with connectivity} : We
+	drew atomistic structures using MarvinSketch 17.13 with all hydrogen atoms
+	drawn out explicitly. We optimized the 3D geometry of the structure using the
+	'Clean in 3D' function of MarvinSketch 17.13~\cite{chemaxon_marvinsketch_2017}.
+	We saved the structure as a .mol file, then converted it to .pdb format using
+	Open Babel 2.4.1 \cite{oboyle_open_2011,noauthor_open_nodate}. 
+	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using the .pdb
+	structure file as input, we ran \texttt{antechamber}~\cite{wang_automatic_2006}
+	using the AM1-BCC charge model. The net charge on the monomer is input as -1
+	since the sodium ion will be kept as a separate residue. The output of
+	\texttt{antechamber} is used to create Amber topology files with
+	\texttt{LEaP}~\cite{case_ambertools16_2016}. A detailed tutorial can be accessed
+	elsewhere \cite{walker_antechamber_nodate}.
+	\item \textit{Create gromacs topologies from Amber output} : \texttt{LEaP}
+	outputs a .inpcrd and a .prmtop file which are Amber topology files. Using
+	acpype.py \cite{sousa_da_silva_acpype_2012}, we convert the \texttt{LEaP}
+	output into GROMACS .gro and .top files. 
+	\item \textit{Perform a simulated annealing procedure on the monomer} :
+	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
+	editconf}. The monomer was centered in the monomer in the box with edges of the
+	box at least 3 nm from the monomer on all sides. We ran an energy minimzation
+	on the system with the steepest descent algorithm.  Next we performed an NVT
+	simulated annealing procedure. We linearly decreased the temperature of the
+	system from 1000K to 50K over the course of 10 ns. We randomly chose a monomer
+	configuration from the last 10 \% of the trajectory. 
+	\item \textit{Reassign charges with \texttt{molcharge}}: With the monomer
+	configuration taken from the annealed trajectory, we reassigned charges using
+	\texttt{molcharge} using the am1bccsym method in order to ensure charges 
+	are symmetric. This condition is not guaranteed with \texttt{antechamber}. 
+	The charges in the gromacs topology file (.top) were replaced with the 
+	new charges calculated by \texttt{molcharge}. 
+	\item \textit{Anneal again to get final structure} : The same simulated
+	annealing process was repeated using the monomer topology with
+	\texttt{molcharge} charges. A random monomer configuration was pulled from
+	the last 10 \% of the trajectory and was used to build all assemblies
+	reported (Figure~\ref{fig:monomer}).
   \end{enumerate}
@@
 
+\bibliography{llc.bib}
 \end{document}

### 2018-01-05 Ben_Manuscripts/structure_paper/supplemental.tex
10 dbwl updated

@@
 
-          We tested 3 different initial layer spacings, defined as the distance between the planes of 
-          aromatic rings in each layer. Systems built with layers stacked 3.7 \AA and 5 \AA apart
-	  are discussed extensively in the main text. We will focus the discussion here on systems
-	  built with layers stacked 10 \AA apart.
+	  We tested 3 different initial layer spacings, defined as the distance
+	  between the planes of aromatic rings in each layer. Systems built with layers
+	  stacked 3.7 \AA and 5 \AA apart are discussed extensively in the main text. We
+	  will focus the discussion here on systems built with layers stacked 10 \AA
+	  apart.
+
+	  Figure ~\ref{fig:dbwl_10} shows the structure of an assembly built
+	  with an initial layer spacing of 10 \AA immediately after the restrained
+	  portion of the equilibration procedure. Since position restraints, the
+	  simulations are run in the NVT ensemble. When layer spacing is large, such as
+	  this situation, there is a significant amount of vacuum space which the monomer
+	  attempts to fill.  Even if turning pressure control on allows the system to
+	  recover the geometry of the hexagonal phase, we would likely need much longer
+	  equilibration times, and it will almost certainly remain trapped in metastable
+	  configurations that bear no resemblence to experimental profiles.
+
+	  \begin{figure}
+		\centering
+		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
+		\caption{}\label{fig:dbwl_10} 
+	  \end{figure}
 

### 2018-01-09 Ben_Manuscripts/structure_paper/Draft.tex
Minor edits to draft and additions to supplemental information
New and updated figures along with major reworks to figure captions

@@
 		\centering
-		\includegraphics[width=\textwidth]{NaGA3C11.png}
+		\includegraphics[width=\textwidth]{NaGA3C11.eps}
 		\caption{}~\label{fig:monomer}
@@
 		\centering
-		\includegraphics[width=\textwidth]{wedge.png}
+		\includegraphics[width=\textwidth]{wedge_thick.png}
 		\caption{}~\label{fig:wedge}
@@
 		\centering
-		\includegraphics[width=\textwidth]{layer_blender.png}
+		\includegraphics[width=\textwidth]{layer_thick.png}
 		\caption{}~\label{fig:wedge_layer}
@@
 
-  % BJC: TODO: Make new rendering of wedges
-  %            Change color scheme 
   \begin{figure}
@@
 		\centering
-		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
+		\includegraphics[width=\textwidth]{cartoon_pore.png}
 		\caption{}~\label{fig:undetailed_pore}
@@
 	\end{subfigure}
-  \caption{Our previous level of understanding of the pore structure (a) only allows us to speculate
-	   about transport behavior in the pore. A detailed molecular model (b) will allow us to
-	   directly observe solute transport. Here, four stacked layers of 5 NA-GA3C11 monomers
-           are pictured from atomistic simulations. The hydrophilic region is in red and the 
-	   hydrophobic region is colored blue.}~\label{fig:detail}
+  \caption{We can only speculate about solute behavior inside the membrane
+	  pores based on our previous picture of the pore structure (a). We will use a
+	  detailed molecular model in order to appropriately model the pore's complex
+	  architecture which is crucial to understanding the mechanism of solute
+	  transport (b). The head group region is colored blue
+	  and the tail region is colored cyan in both representations.}~\label{fig:detail}
   \end{figure}
@@
 	corresponding to a real space separation of 3.7 \angstrom~. Previous
-	work~\ref{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
+	work~\cite{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
 	stacking between aromatic rings in the direction perpendicular to the membrane
@@
                 \centering
-                \includegraphics[width=\linewidth]{WAXS_annotated.png} 
+                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                 \caption{}\label{fig:WAXS}
         \end{subfigure}
-%MRS3: would be good to have all feature labels agree: either can edit to put the names on, or have a key relating numbers to the names you use.
-%BJC2: I will annotate it with the names R-pi, R-alkanes etc. Is that what you mean?
-%MRS4: that works fine.  We just need a way to connect what is in the figure with the names used in the text.  Ideally there would not be two sets of labels, just one.
-%BJC3: Got it, will do once I have more time to focus on figures 
+%BJC: What do you think of the labels now? I tried to make it more clear what each label refers
+% to graphically. I can't decide if it's too cluttered. An alternative is to number them as  
+% I had them before, and then define them in a little box inset to the figure
 	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
 		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
-		packing. The leading peak represents the distance between the
+		packing. The leading peak, q*, represents the distance between the
 		d\textsubscript{100} planes. Using this distance, we know that the distance
-		between pore centers is 4.12 nm. (b) 2D wide angle X-ray scattering gives
-		details about repeating features less than 1 nanometer apart. Experimentalists
-		have justified each of the 5 major reflections present as follows: (I) Aromatic
-		head group $\pi-\pi$ stack 3.7 \AA~apart.  (II) Monomers arrange vertically in
-		a 2\textsubscript{1} helix. (III) Alkane chain tails pack 4.5 \AA~apart. (IV)
-		Monomer tails tilt with respect to the membrane plane. (V) As derived from
+		between pore centers is 4.12 nm. (b) 2D WAXS gives
+		details about repeating features on the order of angstroms. Experimentalists
+		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
+		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-helix) Monomers arrange vertically in
+		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
+		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
 		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
@@
   We parameterized the liquid crystal monomers using the Generalized AMBER
-  Forcefield \cite{wang_development_2004} with the Antechamber package
+  Force Field \cite{wang_development_2004} with the Antechamber package
   \cite{wang_automatic_2006} provided with AmberTools16
@@
 	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
-		configuration. (b) Python scripts rotate and assemble monomers into layers with 
+		configuration. (b) A python script rotates and assembles monomers into layers with 
 		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
@@
 	\includegraphics[width=\linewidth]{p2p.png}
-	\caption{Systems built with 5 monomers per layer in a parallel
-		displaced configuration result in a pore spacing closest to the experimental
-		value of 4.12 nm. The pore spacing of the model increases as number of monomers
-		in each layer increases. The pore spacing of a system starting in the
-		sandwiched configuration is systematically slightly lower than that started in
-		an offset configuration. }~\label{fig:p2p}
+	\caption{When we build systems with 5 monomers per layer in the
+		parallel displaced configuration, the equilibrated pore spacing is closest to
+		the experimental value of 4.12 nm. The equilibrated pore spacing of the model
+		increases as the number of monomers in each layer increases. The pore spacing
+		of systems starting in the sandwiched configuration is systematically slightly
+		lower than those started in the parallel displaced configuration.}~\label{fig:p2p}
   \end{figure}
@@
         \end{subfigure}
-        \caption{Pair distribution functions of aromatic carbons for the
-        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
-        parallel displaced configurations. Clear periodic maxima in the
-        $z$ number density indicate distinct layers. The magnitude
-        of the spikes with respect to the average suggest that the 5
-        monomer per layer, sandwiched configuration possesses a higher
-        degree of layer partitioning.}\label{fig:zdf}
+	\caption{We support the existence of layers with the observance of
+		clear periodic maxima in the $z$-direction pair distribution functions of the
+		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
+		displaced configurations. The extent to which we consider a system to be
+		layered is based on the magnitude of the deviation of the periodic maxima from
+		the average number density. The sandwiched configuration possesses a higher
+		degree of layering than the parallel displaced configuration and, in both
+		cases, the head group region has a higher degree of layer partitioning than the
+		tail region. (See supplemental information for detailed definitions of the head
+		group and tail regions)}\label{fig:zdf}
   \end{figure}
@@
         \vspace{-0.2em}
-        \includegraphics[width=1.018\linewidth]{layered_rzplot.png}
-        \caption{}~\label{fig:rz_layered}
+        \includegraphics[width=1.018\linewidth]{offset_rzplot.png}
+        \caption{}~\label{fig:rz_offset}
   \end{subfigure}
@@
         \centering
-        \includegraphics[width=\linewidth]{offset_rzplot.png}
-        \caption{}~\label{fig:rz_offset}
+        \includegraphics[width=\linewidth]{layered_rzplot.png}
+        \caption{}~\label{fig:rz_layered}
   \end{subfigure}
@@
         \centering
-        \vspace{-3.30em}
+        \vspace{-4.00em}
         \includegraphics[width=\linewidth]{colorbar_jet.png}
   \end{subfigure}
-  \caption{The simulated X-ray diffraction patterns for simulations run in the
-  sandwiched (a) and parallel-displaced (c) configurations are compared to experiment (b). 
-  The parallel displaced configuration is the only one that exhibits all major
-  reflections of interest to some degree}
+  \caption{The simulated XRD pattern generated from the equilibrated trajectory
+	  of the parallel displaced configuration (a) exhibits all major reflections
+	  present in the experimental WAXS pattern (b). The simulated XRD pattern
+	  generated from the equilibrated trajectory in the sandwiched configuration shows
+	  all major reflections except R-helix.}
   \label{fig:XRDsim}
@@
   \includegraphics[width=0.5\linewidth]{tilt_dist.png}
-  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
-  indicates an average tilt angle near 7\degree~which is far from the 37\degree~tilt angle 
+  \caption{We measured the angle made between each monomer alkane tail and the membrane plane. 
+  The average tilt angle is near 7\degree~which is far from the 37\degree~tilt angle 
   previously used to explain R-spots.}~\label{fig:tilt}
@@
 		\centering
+	 	\vspace{-2em}
 		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
@@
 	\end{subfigure}
-	\caption{(a) We removed all atoms except carbon atoms making up the tails from a 
-	sandwiched configuration trajectory. (b) The simulated diffraction pattern of the
+	\caption{(a) We removed all atoms except carbon atoms that constitute the tails from a 
+	sandwiched configuration trajectory. (b) The simulated XRD pattern of the
         tail-only trajectory still shows R-spots}\label{fig:tails}
@@
 	\end{subfigure} 
-  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
-  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
-  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
-  (b) and (d) respectively.}~\label{fig:tail_packing}
+  \caption{We hypothesize that R-spots is the result of ordered tail packing.
+	  Defining the membrane plane to be 0\degree, we
+	  measured the angles between each alkane chain tail centroid and its nearest
+	  neighbor centroids for the equilibrated parallel displaced (a) and sandwiched
+	  (c) configurations. Peaks that appear in each distribution are centered near
+	  $\pm~33\degree$. We radially integrated the simulated XRD patterns of the
+	  parallel displaced and sandwiched configuration within the region bounding
+	  R-alkanes ((b) and (d) respectively).  Peaks appear in the same location as the
+	  angle distributions which corroborates our hypothesis. Further, we note that
+	  the peaks are strongest in both plots associated with the sandwiched
+	  configuration. As shown in Figure \ref{fig:rz_layered}, systems simulated in
+	  the sandwiched configuration exhibit more intense R-spots
+	  reflections.}~\label{fig:tail_packing}
   \end{figure}
@@
         \end{subfigure}
-	\caption{In comparison to the ordered pore systems, the simulated
-		X-ray diffraction patterns of the parallel displaced (a) and sandwiched (b)
-		configurations are different than the disordered pore systems , most notably in
-		the region bounded by R-alkanes.  When layers are initially stacked further
-		apart, the distance between layers increases (c) and the pore spacing decreases
-		(d).}
+	\caption{There are distinct differences between the disordered and ordered pore systems. 
+		When layers are initially stacked 5\AA~ apart, the distance
+		between layers increases (a) and the pore spacing decreases (b) in comparison to
+		the ordered pore systems. The simulated
+		XRD patterns of disordered pore systems are also appreciably different, most 
+		notably in the region bounded by R-alkanes. The disordered pore
+		systems started in the parallel displaced configuariton (c) does not show R-spots
+		or R-$\pi$ which suggests that head groups are not associating with each other
+		and tails are distributed nearly isotropically. The disordered pore system
+		started in the sandwiched configuration (d) does not show R-$\pi$ but R-spots 
+		is present in different locations because the tails are packed in a different
+		motif.}
   \end{figure}
@@
 	  concentrations of ions and head groups near the pore center, implying a more
-	  uniform, disordered pore.  }~\label{fig:densities}
+	  uniform, disordered pore.}~\label{fig:densities}
   \end{figure}

### 2018-01-09 Ben_Manuscripts/structure_paper/Draft.tex
More figure/caption updates

@@
   	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
-  	\rowname{parallel displaced}&
+  	\rowname{Parallel Displaced}&
   	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_1.png}&
@@
   	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
-  	\rowname{sandwiched}&
+  	\rowname{Sandwiched}&
   	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_1.png}&
@@
   	\end{tabular}
-  	\caption{Simulated diffraction patterns generated from trajectories of systems 
-  	built in the parallel displaced and sandwiched configurations as a function
-  	of water content shows weaker reflections than the dry system.}%
+	\caption{Simulated XRD patterns indicate that systems with added water
+		are not as structured as the dry systems. As increasing amounts of water are 
+		added to both systems, R-$\pi$ fades. When 2.5 wt\% water is added to the
+		sandwiched system, R-$\pi$ gains back some intensity, but its magnitude is not
+		greater than the dry system. R-spots also disappears as water is added. It is
+		absent in all parallel displaced simulations, but fades gradually as water is
+		added to the sandwiched configuration.}%
   \label{fig:solvation}
@@
 
-  %BJC: TODO: Bigger fonts
   \begin{figure}
@@
   \caption{Water fills the membrane pores in the parallel displaced (a) and
-  sandwiched (b) configurations. Sodium ions are distributed fairly uniformly
-  within the pore region, defined by a radius of 0.6 nm.}
+	  sandwiched (b) configurations. We define the pore region to be within 0.6 nm of
+	  the pore center. Head groups in the sandwiched configuration sit closer to the
+	  pore center than they do in the parallel displaced configuration. The parallel
+	  displaced pores are composed primarily of water close to the pore center.}
   \label{fig:water_density}
@@
         \includegraphics[width=0.5\linewidth]{IC_offset.png}
-        \caption{Calculated ionic conductivity using the Nernst-Einstein relation
-        and Collective Diffusion model agree with error. Both methods give calculated
+        \caption{The collective diffusion model and the nernst-einstein relation yield
+        agreeing values of ionic conductivity. Both methods give calculated
         values of ionic conductivity an order of magnitude higher than the experimental
@@
   \end{subfigure}
-  \caption{(a) Reflections produced by the cross-linked configuration fade
-	  relative to the uncross-linked system. The colorbar shown is the same used for
-	  the uncross-linked system. (b) The ionic conductivity is smaller relative to the
-	  uncross-linked system, but still much larger than the experimental value. When
-	  the system is cross-linked, The distance between layers increases (c) and the
-	  pore spacing decreases (d)}~\label{fig:xlink}
+  \caption{Applying our simulated crosslinking mechanism to an equilibrium
+	  configuration causes slight changes to the system's physical and structural
+	  properties. (a) Reflections produced by the cross-linked configuration are
+	  faded relative to the uncross-linked system. (b) The ionic conductivity is
+	  smaller relative to the uncross-linked system, but still much larger than the
+	  experimental value. When the system is cross-linked, the distance between
+	  layers increases (c) and the pore spacing decreases (d)}~\label{fig:xlink}
   \end{figure}

### 2018-01-09 Ben_Manuscripts/structure_paper/supplemental.tex
More figure/caption updates

--- 2018-01-05 Ben_Manuscripts/structure_paper/supplemental.tex
@@
   \vspace{1em}
-  Monomers were parameterized according to the following procedure:
+  We parameterized monomers according to the following procedure:
   \begin{enumerate}
 	\item \textit{Create monomer structure file with connectivity} : We
-	drew atomistic structures using MarvinSketch 17.13 with all hydrogen atoms
-	drawn out explicitly. We optimized the 3D geometry of the structure using the
-	'Clean in 3D' function of MarvinSketch 17.13~\cite{chemaxon_marvinsketch_2017}.
-	We saved the structure as a .mol file, then converted it to .pdb format using
-	Open Babel 2.4.1 \cite{oboyle_open_2011,noauthor_open_nodate}. 
-	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using the .pdb
-	structure file as input, we ran \texttt{antechamber}~\cite{wang_automatic_2006}
-	using the AM1-BCC charge model. The net charge on the monomer is input as -1
-	since the sodium ion will be kept as a separate residue. The output of
-	\texttt{antechamber} is used to create Amber topology files with
-	\texttt{LEaP}~\cite{case_ambertools16_2016}. A detailed tutorial can be accessed
-	elsewhere \cite{walker_antechamber_nodate}.
-	\item \textit{Create gromacs topologies from Amber output} : \texttt{LEaP}
-	outputs a .inpcrd and a .prmtop file which are Amber topology files. Using
-	acpype.py \cite{sousa_da_silva_acpype_2012}, we convert the \texttt{LEaP}
-	output into GROMACS .gro and .top files. 
+	drew atomistic structures using MarvinSketch
+	17.13~\cite{chemaxon_marvinsketch_2017} with all hydrogen atoms drawn out
+	explicitly. We optimized the 3D geometry of the structure using the 'Clean in
+	3D' function of MarvinSketch.  We saved the structure as a .mol file, then
+	converted it to .pdb format using Open Babel 2.4.1
+	\cite{oboyle_open_2011,noauthor_open_nodate}. 
+	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using
+	the .pdb structure file as input, we ran
+	\texttt{antechamber}~\cite{wang_automatic_2006} using the AM1-BCC charge model.
+	The net charge on the monomer is input as -1 since the sodium ion we keep it as
+	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools_nodate} and the
+	output of \texttt{antechamber} to create Amber topology files. A detailed
+	tutorial can be accessed elsewhere \cite{walker_antechamber_nodate}.
+	\item \textit{Create gromacs topologies from Amber output} : The output
+	of \texttt{LEaP} is a .inpcrd and a .prmtop file which are Amber topology
+	files. Using acpype.py \cite{sousa_da_silva_acpype_2012}, we converted the
+	\texttt{LEaP} output into GROMACS .gro and .top files. 
 	\item \textit{Perform a simulated annealing procedure on the monomer} :
 	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
-	editconf}. The monomer was centered in the monomer in the box with edges of the
-	box at least 3 nm from the monomer on all sides. We ran an energy minimzation
+	editconf}. The monomer was centered in the box with edges of the
+	box spaced at least 3 nm from the monomer on all sides. We ran an energy minimzation
 	on the system with the steepest descent algorithm. Next we performed an NVT
@@
 	configuration taken from the annealed trajectory, we reassigned charges using
-	\texttt{molcharge} using the am1bccsym method in order to ensure charges 
+	\texttt{molcharge} with the am1bccsym method in order to ensure charges 
 	are symmetric. This condition is not guaranteed with \texttt{antechamber}. 
-	The charges in the gromacs topology file (.top) were replaced with the 
+	The charges in the GROMACS topology file (.top) were replaced with the 
 	new charges calculated by \texttt{molcharge}. 
-	\item \textit{Anneal again to get final structure} : The same simulated
-	annealing process was repeated using the monomer topology with
-	\texttt{molcharge} charges. A random monomer configuration was pulled from
-	the last 10 \% of the trajectory and was used to build all assemblies
-	reported (Figure~\ref{fig:monomer}).
+	\item \textit{Anneal again to get final structure} : We repeated the
+	same simulated annealing procedure using the monomer topology with
+	\texttt{molcharge} charges. A random monomer configuration was pulled from the
+	last 10 \% of the trajectory and was used to build all assemblies reported
+	(Figure~\ref{fig:monomer}).
   \end{enumerate}
@@
 
-  Any major dependence on initial configuration is addressed in the main text.
+  \vspace{1em}
+  We addressed any major dependence on initial configuration in the main text.
   There we showed that systems are stable when made with 4, 5, 6, 7, and 8
@@
   only tested systems built with 5 monomers per layer with layers stacked in 
-  the parallel displaced configuration. All systems were equilibrated according
+  the parallel displaced configuration. We equilibrated all systems according
   to the dry equilibration procedure.
@@
 	  distance between the central axis of each pore with all others. To reduce the
-	  number of variables, we held the pore radius constant, at 5 \AA~and the
+	  number of variables, we held the pore radius constant, at 6 \AA~and the
 	  distance between layers at 3.7 \AA~since those were the values used in our
@@
 
-	  	\item 39 \AA~: A pore spacing of 39 \AA~is used in order to have a test system
-		started with a spacing below the experimental value. As soon as the restraining
+	  	\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to have a test system
+		with an intial spacing below the experimental value. As soon as the restraining
 		potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the columns are able to
@@
 
-		\item 41 \AA~: A pore spacing of 41 \AA~is chosen since it closely matches the
-		experimental pore spacing.  Again, we observe abrupt repulsion of columns once
-		the restraining potential is switched to 56 KJ mol$^{-1}$ nm$^{-2}$
-		(Figure~\ref{fig:p2p_41}).
+		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
+		it closely matches the experimental pore spacing. Again, we observe abrupt
+		repulsion of columns once the restraining potential is switched to 56 KJ
+		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}).
 
@@
 		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
-		changes erratically until it begins to settle once the force constants are
+		changes erratically until it begins to settle when the force constants are
 		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
-		avoiding a system such as this where vacuum gaps are introduced unnecessarily.
+		avoiding a system such as this where vacuum gaps between pore columns are
+		introduced unnecessarily.  The system equilibrates to a pore spacing of 4.27
+		$\pm$ 0.06 nm.
 
@@
 			change in pore spacing when the position restraints are reduced to 56 KJ
-			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA apart (c) the pore spacing
-			remains relatively stable. When pores are spaced 50 \AA apart (d), the pore
+			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA~apart (c) the pore spacing
+			remains relatively stable. When pores are spaced 50 \AA~apart (d), the pore
 			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
-			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA apart (e), so that monomers
+			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA~apart (e), so that monomers
 			do not intersect with adjacent pores, and position restraints are reduced to 56
-			KJ mol$^{-1}$ nm$^{-2}$, pore spacing changes erratically before stabilizing
-			when force constants are reduced to 3 KJ mol$^{-1}$ nm$^{-2}$.} 
+			KJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
+			when force constants are reduced below 3 KJ mol$^{-1}$ nm$^{-2}$.} 
 		\label{fig:p2p}
@@
 	  3.7 \AA. Equilibrated values of pore radii are presented in
-	  Table~\ref{table:radii}. The pore radius in each frame is calculated as the
+	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated as the
 	  average distance of all carbonyl carbons (See
@@
 	  Statistics for the pore radii reported were generated from the timeseries
-	  representing the average pore radius at each frame.  Equilibration was detected
-	  using \texttt{pymbar.timeseries.detectEquilibration}. The average and standard
-	  deviation of pore radii were calculated using only data points collected after
+	  representing the average pore radius at each frame.  We detected equilibration 
+	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
+	  and standard deviation of pore radii using only data points collected after
 	  equilibration was detected.
@@
 
-          We tested 3 different initial layer spacings, defined as the distance between the planes of 
-          aromatic rings in each layer. Systems built with layers stacked 3.7 \AA and 5 \AA apart
-	  are discussed extensively in the main text. We will focus the discussion here on systems
-	  built with layers stacked 10 \AA apart.
+	  We tested 3 different initial layer spacings, defined as the distance
+	  between the planes of aromatic rings in each layer. Systems built with layers
+	  stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
+	  will focus the discussion here on systems built with layers stacked 10~\AA
+	  apart.
+
+	  Figure~\ref{fig:dbwl_10} shows the structure of an assembly built
+	  with an initial layer spacing of 10 \AA~immediately after the restrained
+	  portion of the equilibration procedure. Since we used position restraints, the
+	  simulations were run in the NVT ensemble. When layer spacing is large, such as
+	  this situation, there is a significant amount of vacuum space which the monomer
+	  attempts to fill. Even if turning pressure control on allows the system to
+	  recover the geometry of the hexagonal phase, we would likely need much longer
+	  equilibration times, and it will almost certainly get trapped in a metastable
+	  configuration that bears no resemblence to the experimental profile.
+
+	  \begin{figure}
+		\centering
+		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
+		\caption{When layers are initially stacked 10 \AA~apart and the system
+                is equilibrated using the dry equlibration procedure, large vacuum gaps
+		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
+	  \end{figure}
 
@@
 
+\clearpage
 \bibliography{llc.bib}

### 2018-01-09 Ben_Manuscripts/structure_paper/supplemental.tex
Added new figures

@@
 
-		\item 2.5 \AA~: The smallest pore radius that we can achieve before energy 
-		minimization becomes problematic is 2.5 \AA.
+		\item 2.5 \AA~: The smallest pore radius that we can achieve
+		before energy minimization becomes problematic is 2.5 \AA. After being run
+		through the full dry equilibration procedure, the average pore radius is 0.40
+		$\pm$ 0.01 \AA.
 
-		\item 5 \AA~:
+		\item 5 \AA~: We tested a pore radius of 5 \AA~because it is
+		slightly larger than the equilibrated pore radius of the system simulated with
+		an intial pore radius of 2.5 \AA. After being run through the full dry
+		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
+		agrees with the 2.5 \AA~ configuration within error.
 
-		\item 8 \AA~: The largest pore radius that can achieve before energy minimization
-		becomes problematic is 8 \AA.
+		\item 8 \AA~: The largest pore radius that can achieved before
+		energy minimization becomes problematic is 8 \AA. One should use caution with
+		such a structure because of the relatively large vacuum space that is created
+		in the pore region of the initial configuration. After being run through the
+		full dry equilibration procedure, we see a combination of cylindrical and
+		slit-like pores (Figure~\ref{fig:slits}). We are wary of such a non-symmetric
+		structure and choose not to use a pore radius of 8 \AA for our starting configurations.
+
 	  \end{enumerate}
@@
 	  % BJC: to be updated once simulations are run out long enough
-	  2.5 \AA & $0.394 \pm 0.002$ \AA \\
-	  5 \AA   & $0.423 \pm 0.002$ \AA \\ % final result
-	  8 \AA   & $0.721 \pm 0.002$ \AA \\
+	  2.5 \AA & $0.40 \pm 0.01$ \AA \\
+	  5 \AA   & $0.42 \pm 0.01$ \AA \\ % final result
+	  8 \AA   & $0.69 \pm 0.01$ \AA \\
 	  \bottomrule
 	  \end{tabular}
-	  \caption{Caption of the future!}~\label{table:radii}
+	  \caption{The average pore radii of systems built with an initial pore
+		  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
+		  the pore radius is too large, slit pores may form.}~\label{table:radii}
 	  \end{table}
+
+	  \begin{figure}
+	  \centering
+          \includegraphics[width=\textwidth]{slit_pores.png}
+	  \caption{A system that was built with an initial pore radius of 8
+		  \AA~equilibrates to a structure that exhibits both cylindrical and slit-like
+		  pores. As pictured here, sodium ions are colored blue, carbon atoms in the
+		  aromatic ring of the head group are colored orange and all else is colored
+		  cyan.}~\label{fig:slits}
+	  \end{figure}
 

### 2018-01-09 llclib/physical.py

@@ -10,6 +10,7 @@ import matplotlib.path as mplPath
 import mdtraj as md
 from random import randint
 from pymbar import timeseries
+import tqdm
 
 
 class region:
@@ -278,21 +279,28 @@ def limits(pos, pcenters):
 
     nT = pcenters.shape[2]
     npores = pcenters.shape[1]
-    natoms= pos.shape[1]
+    natoms = pos.shape[1]
     atom_ppore = old_div(natoms, npores)
 
     deviation = np.zeros([nT, npores, atom_ppore])
-    for f in range(nT):
+    for f in tqdm.tqdm(range(nT)):
         for i in range(atom_ppore):
             for j in range(npores):
-                deviation[f, j, i] = np.linalg.norm(pos[f, j*atom_ppore + i, :2] - pcenters[:, j, f])  # left off here
+                deviation[f, j, i] = np.linalg.norm(pos[f, j*atom_ppore + i, :2] - pcenters[:, j, f])
 
-    deviation = np.reshape(deviation, (nT, natoms))
+    #deviation = np.reshape(deviation, (nT, natoms))
+
     fr = np.zeros([nT])
     frstd = np.zeros([nT])
+    #
+    # for i in range(nT):
+    #     fr[i] = np.mean(deviation[i, :])  # + np.std(deviation[i, :]) # maybe?
+    #     frstd[i] = np.std(deviation[i, :])
 
-    for i in range(nT):
-        fr[i] = np.mean(deviation[i, :])  # + np.std(deviation[i, :]) # maybe?
-        frstd[i] = np.std(deviation[i, :])
+    radii = np.zeros([nT, npores])
 
-    return fr, frstd
+    for t in range(nT):
+        for p in range(npores):
+            radii[t, p] = np.mean(deviation[t, p, :])
+
+    return radii

### 2018-01-19 Ben_Manuscripts/structure_paper/Draft.tex
Added new figures
More analysis scripts and figures

@@
   \maketitle
+
+  \begin{abstract}
+
+  Nanostructured porous membranes made from the cross-linked hexagonal phase of
+  self-assembled lyotropic liquid crystals (LLCs) are a promising material for
+  selective separations. To date, their separation performance has only been
+  characterized with membranes made from a small set of LLC monomers. There
+  remains a large design space that we can likely exploit to design membranes for
+  solute specific separations. In this work, we develop an atomistic molecular
+  model of an LLC membrane. We show that our model is maximally consistent with
+  experimental observations by comparing simulated X-ray Diffraction (XRD)
+  patterns and calculated ionic conductivity to their experimental counterparts.
+  We explore, in depth, the composition and structure of the nanopores in order
+  to give insights that are not easily accessible to experimentalists. With the
+  clear picture of the nanoscopic structure of these membranes gained from this
+  work, we will be able to use the model to understand the mechanisms of small
+  charged and uncharged solute transport within the nanopores, and eventually we
+  will be able to screen large sets of modified monomers with their separation
+  properties in mind.
+
+  \end{abstract}
 
@@
 
-  \item What constitutes a pore, and how well-defined are the pore regions? \label{point:poredefinition}
+  %\item What constitutes a pore, and how well-defined are the pore regions? \label{point:poredefinition}
+  \item What constitutes a pore, and what does the pore architecture look like? \label{point:poredefinition}
 
@@
   a reasonable value (See Supplemental Information). The pore radius is chosen to
-  be 0.6 nm in our initial configurations because the pore size is estimated to
-  be $\sim$1.2 nm \cite{zhou_supported_2005}. The initial distance between pores
+  be 0.5 nm in our initial configurations. The initial distance between pores
   also has little effect on the the equilibrated structure (See supplemental
@@
 
-  \subsection{Determining Definition of Layers}
+  \subsection{Layer partitioning}
 
   We learned that layers are well-defined and persistent, answering
-  (\ref{point:layers}). We established our conclusion by plotting the pair
-  correlation function, $g(z)$, calculated between atoms along the length of the
+  (\ref{point:layers}). We established our conclusion by plotting the one dimensional pair
+  distribution function, $g(z)$, calculated between atoms along the length of the
   pores (Fig.~\ref{fig:zdf}). We measured $g(z)$ with respect to aromatic rings in
@@
   configuration layers stack 4.38 \angstrom~apart.
+
+  Insert paragraph about 2D pair distribution function (yz cross section).
+
+  We measured the correlation length, L, by fitting a function of the form:
+  $$1 + Asin(Bx + C)e^{-z/L}$$ where z is the independent variable and all
+  other variables are fitting parameters. The correlation length for each
+  system is given in Table~\ref{fig:correlation_length}.
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{ccc}
+  \toprule
+  System & Layer Separation & Correlation Length \\
+  \midrule
+  Sandwiched & 4.39 \AA & 41 $\pm$ 3 \AA \\
+  Parallel Displaced & 4.38 \AA & 86 $\pm$ 14 \AA \\
+  Experiment* & 3.7 \AA & 32 $\pm$ 1 \AA \\  
+  \bottomrule
+  \end{tabular}
+  \caption{*See supplemental information for derivation of experimental correlation length}~\label{fig:correlation_length}
+  \end{table}
 
@@
   configuration, suggesting that we have found another metastable free energy
-  basin, further corroborating (\ref{point:metastable}). For reasons to become
-  apparent later, we will refer to this class of systems as the disordered pore
-  basin. Systems which we build with layers initially stacked 3.7 \AA~apart will
-  be referred to as the ordered basin. We studied each basin in both the parallel
-  displaced and sandwiched configurations.
-
-%  Structural properties are different when layers are initially spaced 5 \AA~
-%  apart. 
-  Structural properties are different in the disordered pore basin.  In both
-  configurations, we observe a decrease in pore spacing
-  (Fig.~\ref{fig:p2p_disordered}) and a corresponding increase in the
-  equilibrated distance between layers (Fig.~\ref{fig:dbwl_disordered}). The
-  simulated X-ray diffraction patterns indicate further structural differences.
-  In the parallel displaced configuration, almost all contrast between R-spots
-  and R-alkanes fades (Fig.~\ref{fig:offset_disordered_xrd}). In the
-  sandwiched configuration, R-spots is weakly present, but in different
+  basin, further corroborating (\ref{point:metastable}). The basins are
+  differentiated by their relative degrees of ordering resulting from different
+  spatial arrangements.
+
+  We expect that the head groups in more ordered systems will be predominantly
+  coplanar with the xy plane. We defined a director vector, \textbf{n}, as the
+  vector normal to the plane of the monomer's aromatic head group, then measured
+  the distribution of angles between it and the z-axis. We used the resulting
+  distibution of angles to calculate the nematic order parameter, S. The values
+  of S for systems resulting from each initial configuration are presented in
+  Table \ref{table:nematic}. The full distributions of angles between \textbf{n}
+  and the z-axis are presented in the supplemental material. In general, systems
+  started with layers spaced 3.7 \AA apart are more nematically ordered than
+  those initially spaced 5 \AA apart. We will refer to systems built with layers
+  initially spaced 3.7 \AA apart and 5.0 \AA apart as the ordered and disordered
+  pore basins respectively. We studied each basin in both the parallel displaced
+  and sandwiched configurations.
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cc}
+  \toprule
+  System & Nematic Order Parameter (S) \\
+  \midrule
+  Sandwiched, Ordered & 0.659 $\pm$ 0.003 \\
+  Parallel Displaced, Ordered & 0.601 $\pm$ 0.003 \\
+  Sandwiched, Disordered & 0.565 $\pm$ 0.002 \\
+  Parallel Displaced, Disordered & 0.503 $\pm$ 0.002 \\
+  \bottomrule
+  \end{tabular}
+  \caption{The nematic order parameter is higher when layers are initially spaced
+  3.7 \AA apart. A perfectly stacked system with aromatic rings coplanar with the
+  xy plane would have a nematic order parameter of 1, while isotropically aligned
+  director vectors would have a nematic order parameter of 0.}~\label{table:nematic}
+  \end{table}
+
+  We observe more evidence of disorder in the disordered pore basin when we 
+  plot the two dimensional pair distribution function between the centers of 
+  mass of monomer head groups. ADD MORE ANALYSIS ONCE CODE IS WORKING HOW I WANT IT
+
+  \begin{figure}
+  \begin{subfigure}{1\linewidth}
+        \centering
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{layered_xy_rings.png}
+                \caption{}~\label{fig:sandwich_xy}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{offset_xy_rings.png}
+                \caption{}~\label{fig:offset_xy}
+        \end{subfigure}
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{disorder_sandwich_xy_rings.png}
+                \caption{}~\label{fig:disorder_sandwich_xy}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{disorder_offset_xy_rings.png}
+                \caption{}~\label{fig:disorder_offset_xy}
+        \end{subfigure}
+  \end{subfigure}
+  \caption{}\label{fig:xy_correlation}
+  \end{figure}
+
+  The simulated X-ray diffraction patterns indicate further structural
+  differences. In the parallel displaced configuration, almost all contrast
+  between R-spots and R-alkanes fades (Fig.~\ref{fig:offset_disordered_xrd}). In
+  the sandwiched configuration, R-spots is weakly present, but in different
   locations, showing higher intensity at the top and bottom of the pattern as
@@
   different head group configurations.
+
+  The equilibrated pore spacing and distance between layers are different in
+  the disordered pore basin. For both head group stacking arrangements, we
+  observe a decrease in pore spacing (Fig.~\ref{fig:p2p_disordered}) and a
+  corresponding increase in the equilibrated distance between layers
+  (Fig.~\ref{fig:dbwl_disordered}).
 
@@
 
-  \subsection{Pore Structure Depends on Initial Configuration}  % Addresses pore definition
+  \subsection{Pore Composition Depends on Initial Configuration}
 
@@
   head groups. In the ordered pore systems, there is less density in the center of
-  the pore indicating a more ordered pore structure. In both the sandwich and
+  the pore indicating a more ordered pore structure. In both the sandwiched and
   parallel displaced configurations, we see the density of head groups and sodium
@@
   Assuming a pore radius of 0.6 nm, we see in all cases, that 19\% of sodium ions
-  exist outside the pore region (except sandwiched, ordered pore , where 16\%
+  exist outside the pore region (except sandwiched, ordered pore, where 16\%
   are outside the pore). Additionally, we see that in all cases, about 3\% of the

### 2018-01-19 Ben_Manuscripts/structure_paper/supplemental.tex
More analysis scripts and figures

@@
 
-  \color{red}{This is an outline of this section and will be reworded for clarity}
-  \begin{itemize}
-  	\item We are interested in 5 pore-to-pore distances which should all
-	be equal in a perfect hexagonal array, however only 4 distances are independent
-	% can visualize this in supplemental material. Will make a lot of things more
-	clear below.
-	\item Each pore spacing has its own trajectory of spacing vs. time.
-	Using data collected after the system is equilibrated, we calculate how long it
-	takes for the data in each of the 5 trajetories to become uncorrelated using
-	pymbar.timeseries.integratedAutocorrelationTime() % reference
-	\item We break the full trajectories down into sub-trajectories based
-	on the maximum autocorrelation time of those found in the previous step.
-	\item For each bootstrap trial, we recreate an equilibrium trajectory
-	by randomly sampling pore spacings from the sub-trajectories 
-	\item We get an average value for each pore spacing by finding the
-	mean of the bootstrapped data
-	\item We calculate the overall average as the mean of all
-	bootstrapped pore spacings
-	\item The uncertainty for each pore spacing is calculated as
-	$\dfrac{<x> - x}{4}$ where $<x>$ is the average spacing from the bootstrap
-	trial and $x$ is the average value of one of the pore spacings.
-	\item We report the mean of these uncertainties
-  \end{itemize}
+  We are interested in 5 pore-to-pore distances which should all be
+  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
+  the 5 distances are independent. We can calculate a trajectory of spacing
+  versus time for each of the 5 distances. We calculated the average pore-to-pore
+  spacing and its uncertainty according to the following procedure:
+   \begin{enumerate}
+	\item We calculated the time when each of the pore-to-pore distances
+	were equilibrated using \texttt{pymbar.timeseries.detectEquilibration()} \\
+	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
+	after the largest of the five values.
+	\item We calculated how long it takes for the data in each of the 5
+	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
+	\cite{chodera_simple_2016,shirts_statistically_2008}. 
+	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
+	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
+	five sub-trajectories of pore-to-pore spacings.   
+	\item We generate statistics using the bootstrapping technique. For
+	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
+	sampling from the trajectory blocks. 
+	\item The average pore-to-pore distance is the mean of all pore
+	spacings among all bootstrap trials.
+	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
+	pore spacing for each pore over all bootstrap trials. Using the 5 average 
+	pore-to-pore distances, we calculate the spread with:
+	\begin{align}
+	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
+	\end{align}
+	where $\overline{x}$ is the average pore-to-pore distance.
+  \end{enumerate}
+
+  \begin{figure}
+	\centering
+	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
+	\caption{There are five pore-to-pore distances that are equal in a perfect
+		hexagonal. If each number in the diagram represents the center of a
+		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
+		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
+		are independent. For example, the distance from 1 to 4 is defined by
+		the location of all other pore centers.}
+	\label{fig:p2p_diagram}
+  \end{figure}
 
@@
   to the dry equilibration procedure.
+
+  \vspace{1em}
+  \begingroup
+	\fontsize{14pt}{12pt}\selectfont
+	\textbf{Experimental correlation length of Ri-$\pi$}
+  \endgroup
+
+  \vspace{1em}
+  Experimentalists did not measure the correlation length, so we estimated it from
+  the raw data. We took a slice of the 2D WAXS data along the dashed line in Figure
+  ~\ref{fig:waxs_dashed}. We removed background noise by subtracting
+  the intensity far from the pattern (high $q$) uniformly. We used a least squares
+  algorithm to fit a lorentzian curve to the data. Only values recorded above $q_z$ = 1.6 were considered for 
+  the fit in order to mitigate interference from R-alkanes (Figure~\ref{fig:correlation_length_exp}).
+  The full width at half maximum (FWHM) is related to the correlation length, L, by
+  the relationship: $ L = \frac{\pi}{FWHM} $. The error in the value is calculated
+  as the square root of the diagonal entry of the covariance matrix calculated 
+  % need citations and more on lorentzian parameters
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.45\textwidth}	
+  	\includegraphics[width=\textwidth]{waxs_dashed.png}
+	\caption{}~\label{fig:waxs_dashed}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
+	\caption{}~\label{fig:correlation_length_exp}
+  \end{subfigure}
+  \caption{}~\label{fig:correlation}
+  \end{figure}
 
@@
 
+  \begin{figure}[ht]
+
+  \begin{subfigure}{\linewidth}
+        \centering
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{layered_nematic_order.png}
+                \caption{Sandwiched, Ordered}~\label{fig:sandwich_nematic}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{offset_nematic_order.png}
+                \caption{Parallel Displaced, Ordered}~\label{fig:offset_nematic}
+        \end{subfigure}
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{disorder_sandwich_nematic_order.png}
+                \caption{Sandwiched, Disordered}~\label{fig:disorder_sandwich_nematic}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{disorder_offset_nematic_order.png}
+                \caption{Parallel Displaced, Disordered}~\label{fig:disorder_offset_nematic}
+        \end{subfigure}
+
+  \end{subfigure}
+  \caption{}~\label{fig:nematic_distribution}
+  \end{figure}
+
   \begin{figure}[!ht]

### 2018-01-19 HII/Scripts/Diffusivity.py

@@ -12,6 +12,7 @@ import Poly_fit
 import mdtraj as md
 import top
 import time
+import Atom_props
 
 
 def initialize():
@@ -19,7 +20,8 @@ def initialize():
     parser = argparse.ArgumentParser(description='Calculate diffusion coefficient')
     parser.add_argument('-t', '--trajectory', default='wiggle.trr', help='Path to input file')
     parser.add_argument('-g', '--gro', default='wiggle.gro', help='Name of .gro coordinate file')
-    parser.add_argument('-r', '--residue', default='SOL', help='Name of residue whose diffusivity we want')
+    parser.add_argument('-r', '--residue', type=str, help='Name of residue whose diffusivity we want')
+    parser.add_argument('-atoms', nargs='+', help='Name of atoms whose collective diffusivity is desired')
     parser.add_argument('--itp', default='/usr/local/gromacs/share/gromacs/top/amber99.ff/tip3p.itp', help='Name of itp'
                         'describing topology of residue')
     parser.add_argument('-b', '--nboot', default=200, help='Number of bootstrap trials to be run')
@@ -157,22 +159,36 @@ def dconst(x, nT, Nbootstraps, frontfrac, fracshow, d, dt, ndx):
 if __name__ == '__main__':
 
     args = initialize()  # initialize variables passed to the script
+    frontfrac = args.frontfrac
+    fracshow = args.fracshow
 
     t = md.load(args.trajectory, top=args.gro)  # load trajectory
     nT = t.n_frames  # number of frames
 
-    res = args.residue
-    if res == 'SOL':  # mdtraj changes the name from SOL to HOH
-        res = 'HOH'
+    if args.residue:
 
-    selection = [a.index for a in t.topology.atoms if a.residue.name == res]
+        res = args.residue
+        if res == 'SOL':  # mdtraj changes the name from SOL to HOH
+            res = 'HOH'
+
+        selection = [a.index for a in t.topology.atoms if a.residue.name == res]
+
+        topology = top.Top(args.itp)  # read topology
+        atoms_per_residue = topology.natoms  # number atoms in a single residue
+        matoms = topology.atom_masses  # mass of the atoms in residue
+        mres = np.sum(matoms)  # total mass of residue
+
[…]

### 2018-01-25 Ben_Manuscripts/structure_paper/Draft.tex
draft updates

@@
 
+  Reverse osmosis (RO) and nanofiltration (NF) are membrane based separation
+  processes widely used to create potable or reusable water by removing salts and
+  other dissolved compounds from water sources. RO membranes are typically thin
+  film composite (TFC) membranes with a porous support layer and a dense
+  crosslinked polymer active layer which near indiscriminately separates all solutes.
+  NF membranes are porous with pores on the order of 1 $\nm$ in size which separate 
+  primarily based on solute size.
+
+  RO and NF are finding applications beyond primarily water-based
+  separation. Recovery of valued products from complex aqueous and organic waste
+  is of increasing interest. This requires highly selective membranes.
+
+%  The permeability-selectivity tradeoff is a well-known problem in the membrane
+%  separations community. It is difficult to increase the permeability of a 
+%  desired molecular or atomic species, while maintaining the same retention of
+%  an undesired species.
+
+%  Current commercial RO and NF membranes suffer from limitations inherent to
+%  their fabrication. Although scalable, each of these two types of membranes has
+%  a degree of stochasticity that makes overcoming the permeability-selectivity
+%  tradeoff a challenge. Namely, it is difficult to increase the permeability of
+%  a desired molecular or atomic species, while maintaining the same retention of
+%  an undesired species \cite{werber_materials_2016}.
+
+  Selective separation by a semipermeable membrane barrier is governed by two
+  steps : barrier entry and transport through the barrier. A solute's ability to
+  enter a membrane barrier is decided by its size, solubility and charge. A solute's
+  size, shape and polarity affect its ability to travel across the barrier. Undesired
+  solutes may still be able to enter the membrane making their diffusion rates
+  relative to desired solutes important. It is important to design the membrane in response
+  to desired and undesired solutes is thus important.
+
+  NF -- pore polydispersity
+  RO -- r0andom walk through polymer voids
+
   Nanostructured porous membrane materials have become increasingly popular for
@@
   technologies.
-
-  Current commercial RO and NF membranes suffer from limitations inherent to
-  their fabrication. Although scalable, each of these two types of membranes has
-  a degree of stochasticity that makes overcoming the permeability-selectivity
-  tradeoff a challenge. Namely, it is difficult to increase the permeability of
-  a desired molecular or atomic species, while maintaining the same retention of
-  an undesired species \cite{werber_materials_2016}.
 

### 2018-01-26 Ben_Manuscripts/structure_paper/Draft.tex
new figures, better intro and more organization

@@
-\documentclass{article}
+\documentclass[journal=jpcbfk,manusciprt=article]{achemso}
+
 \usepackage{graphicx}
@@
 \usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
+\usepackage{amsmath} 
 \usepackage{siunitx}
 \usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\usepackage{cleveref}
-\usepackage{booktabs}
 \usepackage{gensymb}
-\usepackage{float}
-\usepackage{setspace}
-\usepackage{color}
-\doublespacing
-
-\title{Understanding the nanoscale structure of hexagonal phase
-lyotropic liquid crystal membranes}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble
-\and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R.
-Shirts}
+
+\title{Understanding the nanoscale structure of hexagonal phase lyotropic
+liquid crystal membranes}
+\author{Benjamin J. Coscia}
+\author{Michael R. Shirts}
+\email{michael.shirts@colorado.edu}
+\author{Richard D. Noble}
+\author{Douglas L. Gin}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+\alsoaffiliation{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
+\author{Joe Yelk}
+\author{Matthew Glaser}
+\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
+\author{Xunda Feng}
+\affiliation{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
 
@@
 
-  \bibliographystyle{ieeetr}
   \graphicspath{{./figures/}}
-  \maketitle
+
+  \begin{tocentry}
+  \end{tocentry}
 
@@
 
-  Reverse osmosis (RO) and nanofiltration (NF) are membrane based separation
+  Reverse osmosis (RO) and nanofiltration (NF) are membrane-based separation
   processes widely used to create potable or reusable water by removing salts and
@@
   film composite (TFC) membranes with a porous support layer and a dense
-  crosslinked polymer active layer which near indiscriminately separates all solutes.
-  NF membranes are porous with pores on the order of 1 $\nm$ in size which separate 
-  primarily based on solute size.
+  crosslinked polymer active layer which near indiscriminately separates all
+  solutes. NF membranes have porous architectures with pores on the order of 1 nm
+  in size which separate primarily based on solute size
+  \cite{van_der_bruggen_review_2003}.
 
   RO and NF are finding applications beyond primarily water-based
-  separation. Recovery of valued products from complex aqueous and organic waste
-  is of increasing interest. This requires highly selective membranes.
+  purifications. Recovery of valued products from complex aqueous and organic
+  waste is of increasing interest. For example, flowback water (FW) produced
+  during hydraulic fracturing is a complex wastewater full of potentially
+  valuable dissolved organic compounds \cite{dischinger_application_2017}. There
+  is increasing pressure to reuse hydraulic fracturing water rather than dispose
+  of it in order to reduce social and envrionmental impacts as well as cost
+  \cite{theodori_hydraulic_2014}. Rather than dispose of the wastestream
+  generated in the recycling process, we can instead use highly selective
+  membranes in order to successfully recover the useful compounds.
 
@@
   Selective separation by a semipermeable membrane barrier is governed by two
-  steps : barrier entry and transport through the barrier. A solute's ability to
-  enter a membrane barrier is decided by its size, solubility and charge. A solute's
-  size, shape and polarity affect its ability to travel across the barrier. Undesired
-  solutes may still be able to enter the membrane making their diffusion rates
-  relative to desired solutes important. It is important to design the membrane in response
-  to desired and undesired solutes is thus important.
-
-  NF -- pore polydispersity
-  RO -- r0andom walk through polymer voids
-
-  Nanostructured porous membrane materials have become increasingly popular for
-  aqueous separations applications such as desalination and biorefinement because
-  they offer the ability to control pore architecture at the molecular scale,
-  thereby permitting the design of solute-specific separation membranes
-  \cite{humplik_nanostructured_2011}. One can acheive most membrane-based aqueous separations of
-  small molecules using reverse osmosis (RO) or nanofiltration
-  (NF) \cite{van_der_bruggen_review_2003}. While RO and NF have seen many
-  advances in the past few decades, they are far from perfect separation
-  technologies.
+  steps: barrier entry and transport through the barrier. A solute's ability to
+  enter a given membrane barrier is decided by its size, shape, charge, polarity
+  and how those factors combine to interact with the membrane material. The same
+  properties affect the rate at which a solute travels across the barrier. Since
+  undesired solutes may still enter the membrane, their diffusion rates relative
+  to desired solutes are important
+  \cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}. To achieve optimum
+  selectivity, it is necessary to design membranes in a way that one can tune the
+  relative diffusivities of desired and undesired solutes.
+
+  Lyotropic liquid crystals (LLCs) are amphiphilic molecules that have the
+  ability to self-assemble into porous nanostructures \cite{smith_ordered_1997}
+  which can be crosslinked to create mechanically strong membrane films with
+  pores on the order of 1 nm in diameter \cite{zhou_supported_2005}. Unlike
+  commercial NF membranes, LLC membrane pores are uniform in size. Since LLC
+  membranes lack a pore size distribution, they inherently exhibit high
+  selectivity due to their strict molecular weight cut-off (MWCO).  Additionally,
+  the LLCs chosen to make membranes for this application are salts.  The membrane
+  gains a net surface charge when counterions from head groups that line the pore
+  walls escape into the feed solution in order to balance the gradients of
+  concentration and electric potential. This effect, which causes the membrane to
+  repel incoming charged species, is called Donnan exclusion
+  \cite{donnan_theory_1995}.
+
+  The feasiblity of LLC membranes has been demonstrated using LLCs that form
+  the type 1 bicontinuous cubic (Q\textsubscript{I})
+  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
+  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
+  phases (See Figure~\ref{fig:bcc_v_hII}). When separating organic solutes from
+  NaCl, Q\textsubscript{I} phase membrane filtration experiments have shown
+  selectivity 2-3 times higher than commercial RO and 6-12 times higher than
+  commercial NF membranes \cite{dischinger_application_2017}.  When separating a
+  series of various sized dyes, the H\textsubscript{II} phase membrane showed
+  complete rejection of dyes bigger than 1.2 nm in size
+  \cite{zhou_supported_2005}.
+
+  We will focus our current efforts around the H\textsubscript{II} phase since
+  its geometry should give optimal transport performance compared to the
+  Q\textsubscript{I} phase. The H\textsubscript{II} phase forms at room
+  temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
+  packed, straight, hydrophilic pore columns\cite{smith_ordered_1997}. In the
+  absence of water, neat monomer will form the same hexagonal columnar structure
+  which, in literature, has been referred to as the Col\textsubscript{h}
+  thermotropic phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}).
+  These hexagonal columnar phases represent the ideal geometry for membrane
+  transport. The most promising Q\textsubscript{I} phase for membrane
+  applications forms at 70\degree C when monomer is mixed with c.a.~20 wt\%
+  glycerol\cite{carter_glycerol-based_2012}. The Q\textsubscript{I} phase
+  consists of a network of three dimensionally interconnected pores (See
+  Figure~\ref{fig:bcc_phases}). This complex geometry effectively adds a degree
+  of tortuosity to the membrane which prevents optimal through-plane transport.
+  Despite the geometric differences between the Q\textsubscript{I} and
+  H\textsubscript{II} phase, the chemical environment within the pores is
+  expected to be similar, and either membrane should be highly selective.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[trim=-2cm 0 0 0, clip, height=4.5cm]{Dibrpyr14.eps}
+        \includegraphics[height=4.5cm]{bcc_phases.png}
+        \caption{}\label{fig:bcc_phases}
+  \end{subfigure}
+  \hspace{1cm}
+  \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[trim=0 -0.5cm 0 -0.5cm, clip, height=4.5cm]{NaGA3C11.eps}
+        \includegraphics[height=4.5cm]{hexagonal_packing.png}
+        \caption{}\label{fig:hII_phase}
+  \end{subfigure}
+  \caption{The choice of LLC monomer leads to different favorable liquid
+        crystalline phases. The monomer shown in (a) forms the Q\textsubscript{I} phase
+        in either the Ia3d (left) or Pn3m (right) space group. The surfaces shown
+        represent the interface between the hydrophilic and hydrophobic regions of unit
+        cell. As pictured, we assume that each region occupies an equal volume. The
+        monomer shown in (b) will form the hexagonal columnar phase
+        (H\textsubscript{II} in the presence of water or Col\textsubscript{h} when no
+         water is present).}\label{fig:bcc_v_hII}
+  \end{figure}
+
+  %Nanostructured porous membrane materials have become increasingly popular for
+  %aqueous separations applications such as desalination and biorefinement because
+  %they offer the ability to control pore architecture at the molecular scale,
+  %thereby permitting the design of solute-specific separation membranes
+  %\cite{humplik_nanostructured_2011}. One can acheive most membrane-based aqueous separations of
+  %small molecules using reverse osmosis (RO) or nanofiltration
+  %(NF) \cite{van_der_bruggen_review_2003}. While RO and NF have seen many
+  %advances in the past few decades, they are far from perfect separation
 
@@
 
-  Commercial RO membranes are typically dense thin-film composite (TFC)
-  membranes with a porous support layer and an active layer made of a polymer
-  matrix formed through interfacial polymerization \cite{jeong_interfacial_2007}.
-  During interfacial polymerization, a step-growth polymerization reaction occurs
-  at the interface of an aqueous monomer solution that has been soaked into the
-  support layer, and an organic solution of a second monomer. The polymer matrix
-  is dense and highly cross-linked which gives high rejections but low
-  permeability.
+  %Commercial RO membranes are typically dense thin-film composite (TFC)
+  %membranes with a porous support layer and an active layer made of a polymer
+  %matrix formed through interfacial polymerization \cite{jeong_interfacial_2007}.
+  %During interfacial polymerization, a step-growth polymerization reaction occurs
+  %at the interface of an aqueous monomer solution that has been soaked into the
+  %support layer, and an organic solution of a second monomer. The polymer matrix
+  %is dense and highly cross-linked which gives high rejections but low
+  %permeability.
 
@@
 %  During phase inversion, a thin polymer film is precipitated out of a polymer
-  NF membranes are typically porous membranes made by a phase-inversion
-  process. The most widely used phase-inversion process is immersion
-  precipitation, during which one submerges a polymer, dissolved in a solvent, in
-  a non-solvent. A solid, porous polymer membrane is all that remains once all
-  solvent has been removed by non-solvent exchange
-  \cite{smolders_microstructures_1992}.  The resultant pores are polydisperse in
-  size, which hurts membrane selectivity. A second technique used to create NF
-  membranes is call track-etching in which a polymer film is bombarded with
-  charged particles, then chemically etched to create pores
-  \cite{apel_track_2001}. The pores are uniform, which benefits selectivity;
-  however, the membranes have a low porosity and subsequently low permeability.
+
+%  NF membranes are typically porous membranes made by a phase-inversion
+%  process. The most widely used phase-inversion process is immersion
+%  precipitation, during which one submerges a polymer, dissolved in a solvent, in
+%  a non-solvent. A solid, porous polymer membrane is all that remains once all
+%  solvent has been removed by non-solvent exchange
+%  \cite{smolders_microstructures_1992}.  The resultant pores are polydisperse in
+%  size, which hurts membrane selectivity. A second technique used to create NF
+%  membranes is call track-etching in which a polymer film is bombarded with
+%  charged particles, then chemically etched to create pores
+%  \cite{apel_track_2001}. The pores are uniform, which benefits selectivity;
+%  however, the membranes have a low porosity and subsequently low permeability.
 
@@
 
-  The permeability-selectivity tradeoff has the potential to be overcome by
-  designing membranes at the molecular level. Next-generation nanoporous
-  membranes with high selectivity, permitted by a precisely controlled pore size,
-  and high permeability, allowed by its porous architecture, have the potential to
-  replace traditional RO and NF membrane technologies.
+%  The permeability-selectivity tradeoff has the potential to be overcome by
+%  designing membranes at the molecular level. Next-generation nanoporous
+%  membranes with high selectivity, permitted by a precisely controlled pore size,
+%  and high permeability, allowed by its porous architecture, have the potential to
+%  replace traditional RO and NF membrane technologies.
 
@@
 
-  Development of nanostructured porous materials has been limited by the
-  ability to synthesize and scale various fundamentally sound technologies.
-  Graphene sheets are atomically thick which results in excellent water
-  permeability but defects during manufacturing severely impact selectivity
-  \cite{cohen-tanugi_multilayer_2016}. Molecular dynamics (MD) simulations of
-  carbon nanotubes show promise \cite{humplik_nanostructured_2011}, but synthetic
-  techniques are unable to achieve scalable alignment and pore monodispersity
-  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Zeolites have sub-nm
-  pores with a narrow pore size distribution, and MD simulations of these
-  materials show that they exhibit complete rejection of solvated ions
-  \cite{murad_molecular_1998}- however, experimental rejection was low and
-  attributed to interstitial defects formed during membrane synthesis
-  \cite{li_desalination_2004}. Consequently, there is a need for a scalable
-  nanostructured porous membrane.
-
-  Polymeric membranes based on self-assembling lyotropic liquid crystals (LLCs)
-  are suitable candidates for aqueous separation applications. LLCs are
-  amphiphilic molecules that share the characteristic ability of nanostructured
-  porous membrane materials to create highly ordered nanostructures with the
-  added benefits of low cost and synthetic techniques feasible for large-scale
-  production \cite{feng_scalable_2014}. LLC systems created by the monomer
-  Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied experimentally
-  \cite{feng_scalable_2014,smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_thin_2016}.
-  The neat Na-GA3C11 monomer forms the thermotropic liquid crystalline (TLC)
-  Col\textsubscript{h} phase (Fig.\ref{fig:assembly}). The presence of ca. 10
-  wt\% added water results in formation of the lyotropic H\textsubscript{II}
-  phase. In both cases, Na-GA3C11 monomers assembles into mesophases made of
-  hexagonally packed, uniform size, cylinders with hydrophilic head groups
-  oriented inward towards the cylinder center. This LLC assembly is then
-  polymerized in situ to form a cross-linked polymer network to stabilize the
-  structure. The hydrophilic region can act as a pore for aqueous separations
-  \cite{zhou_supported_2005}.  One can envision tailoring the pore region for
-  specific separations by changing the monomer chemistry
-  \cite{resel_h2-phase_2000}.
-
-  Research into polymerized LLC membranes has been revived in recent years.
-  During early stages of exploration, mesophases formed by Na-GA3C11 could not be
+%  Development of nanostructured porous materials has been limited by the
+%  ability to synthesize and scale various fundamentally sound technologies.
+%  Graphene sheets are atomically thick which results in excellent water
+%  permeability but defects during manufacturing severely impact selectivity
+%  \cite{cohen-tanugi_multilayer_2016}. Molecular dynamics (MD) simulations of
+%  carbon nanotubes show promise \cite{humplik_nanostructured_2011}, but synthetic
+%  techniques are unable to achieve scalable alignment and pore monodispersity
+%  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Zeolites have sub-nm
+%  pores with a narrow pore size distribution, and MD simulations of these
+%  materials show that they exhibit complete rejection of solvated ions
+%  \cite{murad_molecular_1998}- however, experimental rejection was low and
+%  attributed to interstitial defects formed during membrane synthesis
+%  \cite{li_desalination_2004}. Consequently, there is a need for a scalable
+%  nanostructured porous membrane.
+
+%  Polymeric membranes based on self-assembling lyotropic liquid crystals (LLCs)
+%  are suitable candidates for aqueous separation applications. LLCs are
+%  amphiphilic molecules that share the characteristic ability of nanostructured
+%  porous membrane materials to create highly ordered nanostructures with the
+%  added benefits of low cost and synthetic techniques feasible for large-scale
+%  production \cite{feng_scalable_2014}. LLC systems created by the monomer
+%  Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied experimentally
+%  \cite{feng_scalable_2014,smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_thin_2016}.
+%  The neat Na-GA3C11 monomer forms the thermotropic liquid crystalline (TLC)
+%  Col\textsubscript{h} phase (Fig.\ref{fig:assembly}). The presence of ca. 10
+%  wt\% added water results in formation of the lyotropic H\textsubscript{II}
+%  phase. In both cases, Na-GA3C11 monomers assembles into mesophases made of
+%  hexagonally packed, uniform size, cylinders with hydrophilic head groups
+%  oriented inward towards the cylinder center. This LLC assembly is then
+%  polymerized in situ to form a cross-linked polymer network to stabilize the
+%  structure. The hydrophilic region can act as a pore for aqueous separations
+%  \cite{zhou_supported_2005}.  One can envision tailoring the pore region for
+%  specific separations by changing the monomer chemistry
+%  \cite{resel_h2-phase_2000}.
+
+  Research into the H\textsubscript{II} phase of polymerized LLC membranes has
+  been revived in recent years. During early stages of exploration, hexagonal
+  mesophases formed by Na-GA3C11 (Figure~\ref{fig:assembly}) could not be
   macroscopically aligned, resulting in low flux membranes, and no clear route
-  towards scalable and economical filtration. In 2014, Feng et al.~showed that
-  one can align the mesophases using a magnetic field with subsequent
-  cross-linking to lock the structure in place \cite{feng_scalable_2014}. In 2016,
-  Feng et al. showed that one could obtain the same result using a second
-  technique termed soft confinement \cite{feng_thin_2016}.
+  towards scalable and economical filtration. For this reason, research efforts
+  focused on the Q\textsubscript{I} phase, whose geometry does not require
+  alignment. In 2014, Feng et al.~showed that one can align 
+  Col\textsubscript{h} mesophases using a magnetic field with subsequent
+  cross-linking to lock the structure in place \cite{feng_scalable_2014}. In
+  2016, Feng et al. showed that one could obtain the same result using a second
+  technique termed soft confinement \cite{feng_thin_2016}. Current efforts are
+  focused on extending the method to the H\textsubscript{II} phase and 
+  characterizing the performance of these newly aligned systems.
 
@@
   counterion used and observed its affect on pore spacing
-  \cite{resel_structural_2000}. In a later study of rejection performance, it
-  was shown that membranes formed by cross-linked Na-GA3C11 in the
-  H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in
-  diameter because the pores are too large \cite{zhou_supported_2005}. We do not
-  yet understand how to controllably reduce the effective pore size or how to
-  tune the chemical environment in the nanopores of this or related materials for
-  effective water desalination and small organic molecule separations. The only
-  source of predictive modeling for LLC systems have been macroscopic models that
-  likely do not adequately describe transport at these length scales
-  \cite{hatakeyama_water_2011}. It will be challenging to efficiently narrow down
-  the large design space in a laboratory setting without a robust model.
-
-  In this study, we build a significantly more realistic atomistic model of LLC
-  membranes than, to our knowledge, has ever previously been done, and explore
-  what new structural information can be gained and what structure hypotheses are
-  supported by this model. We validate the model using as much experimental
-  information as possible. We are most interested in reproducing the conclusions
-  about structure drawn from small angle X-ray scattering (SAXS)
-  and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
-  conductivity measurements \cite{feng_thin_2016}.
+  \cite{resel_structural_2000}. In a later study of rejection performance, it was
+  shown that membranes formed by cross-linked Na-GA3C11 in the
+  H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in diameter
+  because the pores are too large \cite{zhou_supported_2005}. We do not yet
+  understand how to controllably reduce the effective pore size or how to tune
+  the chemical environment in the nanopores of this or related materials for
+  small molecule separations. The only source of predictive modeling for
+  LLC systems have been macroscopic models that likely do not adequately describe
+  transport at these length scales \cite{hatakeyama_water_2011}. It will be
+  challenging to efficiently narrow down the large design space in a laboratory
+  setting without a robust model.
 
@@
   transport and suggest governing mechanisms. We can observe how the choice of
-  head group may influence pore size for size exclusion driven separations. We
-  can interchange counterions which may influence both the pore size and the
-  strength of the Donnan potential which affects the degree to which the membrane
-  can exclude charged species.
+  head group interacts with solutes of interest. We can interchange
+  counterions which may influence both the pore size and the strength of the
+  Donnan potential which affects the degree to which the membrane can exclude
+  charged species at the membrane surface.
+
+  In this study, we build a significantly more realistic atomistic model of LLC
+  membranes than, to our knowledge, has ever previously been created, and explore
+  what new structural information can be gained and what structure hypotheses are
+  supported by this model. We validate the model using as much experimental
+  information as possible. We are most interested in reproducing the conclusions
+  about structure drawn from small angle X-ray scattering (SAXS)
+  and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
+  conductivity measurements \cite{feng_thin_2016}.
 
@@
   A simple molecular simulation study of a similar molecule suggested that
-  there are 4 monomers in each layer \cite{zhu_methacrylated_2006}. Their 
-  model likely does not sufficiently model the chemical environment present
-  in the real system since it only contains 16 total monomers.
-%BJC3: rephrased
-%  However, their estimate is based on a simulated system that contains 16 total
-%  monomers which likely does not sufficiently model the chemical environment
-%  present in the real system
-  A separate calculation based on the estimated volume of the liquid crystal
-  monomers proposes that each layer consists of seven monomers
-  \cite{resel_structural_2000}. Our best chance to answer this question is by
-  using a molecular model orders of magnitude larger than any other reported
-  atomistic liquid crystal membrane simulation, as we present here. We will
-  directly change the layer composition and note its effect on membrane
-  structure.
+  there are 4 monomers in each layer \cite{zhu_methacrylated_2006}. Their model
+  likely does not sufficiently model the chemical environment present in the real
+  system since it only contains 16 total monomers. A separate calculation based
+  on the estimated volume of the liquid crystal monomers proposes that each layer
+  consists of seven monomers\cite{resel_structural_2000}. Our best chance to
+  answer this question is by using a molecular model orders of magnitude larger
+  than any other reported atomistic liquid crystal membrane simulation, as we
+  present here. We will directly change the layer composition and note its effect
+  on membrane structure.
 
@@
 
-  Strong $\pi$-$\pi$ stacking interactions in the direction perpendicular to
-  the membrane plane support the existence of layers experimentally. $\pi$-$\pi$
-  stacking will only occur between the aromatic monomer head groups which leaves
-  no description of what is happening in the monomer tail region. The tails may
-  entangle isotropically while maintaing stacking order among headgroups.
+  Indications of strong $\pi$-$\pi$ stacking interactions in the direction
+  perpendicular to the membrane plane support the existence of layers
+  experimentally. $\pi$-$\pi$ stacking will only occur between the aromatic
+  monomer head groups which leaves no description of what is happening in the
+  monomer tail region. The tails may entangle isotropically while maintaining
+  stacking order among headgroups.
 
@@
   The $\pi$-$\pi$ stacking interactions may be a driving force of self-assembly
-  in this system \cite{gazit_possible_2002}. Gas phase ab initio studies of
-  benzene dimers have shown a clear energetic advantage for parallel displaced
-  and T-shaped $\pi$-$\pi$ stacking conformations over a sandwiched
-  conformation \cite{sinnokrot_estimates_2002}. Substituted benzene rings
-  exhibit an even stronger $\pi$-$\pi$ stacking attraction which favors the
-  parallel displaced configuration in all cases except where the substitutions
-  are extremely electron withdrawing.
-  \cite{waller_hybrid_2006,ringer_effect_2006} In this study, we compare
-  simulated X-ray diffraction patterns to experiment in order to deduce which
-  stacking configuration is most likely.
+  in this system \cite{gazit_possible_2002}. Gas phase \textit{ab initio} studies
+  of benzene dimers have shown a clear energetic advantage for parallel displaced
+  and T-shaped $\pi$-$\pi$ stacking conformations over a sandwiched conformation
+  \cite{sinnokrot_estimates_2002}. Substituted benzene rings exhibit an even
+  stronger $\pi$-$\pi$ stacking attraction which favors the parallel displaced
+  configuration in all cases except where the substitutions are extremely
+  electron withdrawing\cite{waller_hybrid_2006,ringer_effect_2006}. In this
+  study, we compare simulated X-ray diffraction patterns to experiment in order
+  to deduce which stacking configuration is most likely.
 
@@
 
-  %\item What constitutes a pore, and how well-defined are the pore regions? \label{point:poredefinition}
-  \item What constitutes a pore, and what does the pore architecture look like? \label{point:poredefinition}
+  \item What constitutes a pore, and what are the details of its pore architecture? \label{point:poredefinition}
 
@@
   water may play a role in structuring the pores and holding together the
-  hexagonal phase. We can use simulated X-ray diffraction patterns to see if
-  there is any meaningful structural difference between a ``dry'' and ``wet''
-  system.
+  hexagonal phase. We can look at correlation functions and use simulated X-ray
+  diffraction patterns to see if there is any meaningful structural difference
+  between a ``dry'' and ``wet'' system.
 
@@
 
-	\item The location of the first is at $q_z$ = 1.7 \angstrom$^{-1}$,
-	corresponding to a real space separation of 3.7 \angstrom~. Previous
+	\item \textit{R-$\pi$}: The location of the first is at $q_z$ = 1.7
+	\AA$^{-1}$, corresponding to a real space separation of 3.7 \AA~. Previous
 	work~\cite{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
@@
 
-	\item A weak intensity line, located at exactly half the $q_z$ value of
-	R-$\pi$ ($q_z$ = 0.85 \angstrom$^{-1}$), corresponds to a real space periodic
-	spacing of 7.4 \angstrom~. This reflection has been interpreted as
+	\item \textit{R-helix}: A weak intensity line, located at exactly half
+	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
+	space periodic spacing of 7.4 \AA~. This reflection has been interpreted as
 	2\textsubscript{1} helical ordering of aromatic rings along the z axis
@@
 
-	\item A low intensity ring located at r = 1.4 \angstrom$^{-1}$ marks
-	the third major reflection of interest. The real space separation corresponds
-	to 4.5 \angstrom~ which is characteristic of the average spacing between packed
-	alkane chains \cite{mcintosh_organization_1980}. We will call this reflection
-	R-alkanes.
-
-	\item Within R-alkanes, are four spots of higher relative intensity.
-	Accordingly, we name these reflection R-spots. The location of all spots is $\sim 37$
-	degrees from the $q_z$ axis in their respective quadrants. In many liquid
-	crystal systems one can explain the spots by the tilt angle of the alkane chains
-	with respect to the membrane plane \cite{govind_simple_2001}.
-
-	\item The final feature corresponds to the spacing and symmetry of the
-	d\textsubscript{100} plane. This plane is geometrically related the distance
-	between pores. The feature, which we named R-pores, is characterized by dots
-	along the equatorial axis defined when $q_z$ = 0. The spacing between dots is
-	indicative of the hexagonal symmetry of the packed pores. We observe the same
-	information with higher resolution using SAXS (Fig.~\ref{fig:SAXS}).
+	\item \textit{R-alkanes}: A low intensity ring located at r = 1.4
+	\AA$^{-1}$ marks the third major reflection of interest. The real space
+	separation corresponds to 4.5 \AA~ which is characteristic of the average
+	spacing between packed alkane chains \cite{mcintosh_organization_1980}. We will
+	call this reflection R-alkanes.
+
+	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
+	relative intensity.  Accordingly, we name these reflection R-spots. The
+	location of all spots is $\sim 37$ degrees from the $q_z$ axis in their
+	respective quadrants. In many liquid crystal systems one can explain the spots
+	by the tilt angle of the alkane chains with respect to the membrane 
+	plane\cite{govind_simple_2001}.
+
+	\item \textit{R-pores}: The final feature corresponds to the spacing
+	and symmetry of the d\textsubscript{100} plane. This plane is geometrically
+	related the distance between pores. The feature, which we named R-pores, is
+	characterized by dots along the equatorial axis defined when $q_z$ = 0. The
+	spacing between dots is indicative of the hexagonal symmetry of the packed
+	pores. We observe the same information with higher resolution using SAXS
+	(Fig.~\ref{fig:SAXS}).
 
@@
 
-  %BJC: TODO: update colorbar
   \begin{figure}
@@
 
-% Note: we should put scripts and starting configurations (not all that were
-% done but the important ones) in a public repository by the time of
-% submission. 
-%MRS4: I would give a ``plain text'' version of the script in supplementary. BJC: referring to parameterization script
-%MRS4: somewhere would need to specify things like time step tau_t, tau_p, etc., so that people could in theory replicate
-
   \subsection{Unit Cell Preparation}
 
-%MRS4: check grammar additions in this paragraph.
   The timescale for self-assembly of monomers into the hexagonal phase is
@@
 		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
-		pores. (d) The pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
+		pores. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
   \end{figure}
@@
   be 0.5 nm in our initial configurations. The initial distance between pores
-  also has little effect on the the equilibrated structure (See supplemental
-  information). However, one should not start them too close or there will be
+  also has little effect on the the equilibrated structure (See Supplemental
+  Information). However, one should not start them too close or there will be
   high energy repulsions during early equilibration. We chose an initial pore
@@
   \AA. We briefly explored a third system with an initial layer spacing of 10
-  \AA. If we initially space layers too far apart, they will collapse on each
-  other while simultaneously slipping in between layers of adjacent pores, which
-  leads to an artificially thick membrane with pores spaced closely together.
-  Further details of simulations with layer stacked 10 \AA apart are in the supplemental
-  information.
+  \AA, however it shows non-physical behavior which is detailed in the 
+  Supplemental Information.
+
+% This is true if initial equilibration is performed with pressure control
+%  If we initially space layers too far apart, they will collapse on each
+%  other while simultaneously slipping in between layers of adjacent pores, which
+%  leads to an artificially thick membrane with pores spaced closely together.
+%  Further details of simulations with layer stacked 10 \AA apart are in the supplemental
+%  information.
 
@@
   benzene rings: sandwiched, parallel-displaced and T-shaped
-  \cite{sinnokrot_estimates_2002} (Fig. \ref{fig:sandwiched} and
-  \ref{fig:pd,fig:tshaped}).  We ruled out the T-shaped configuration because its
-  $\sim$5 \angstrom~ equilibrium stacking distance
+  \cite{sinnokrot_estimates_2002}. We ruled out the T-shaped configuration
+  because its $\sim$5 \AA~ equilibrium stacking distance
   \cite{sinnokrot_estimates_2002} is inconsistent with R-$\pi$. It is also
@@
   sandwiched vs. parallel displaced stacking modes in some detail. Both have
-  reported stacking distances near the R-$\pi$ value of 3.7 \angstrom. Headgroups
-  in our sandwiched initial configuration stack directly on top of each other
-  while headgroups in the parallel displaced initial configuration stack
-  with an offset of $180/nmon$ degrees where $nmon$ equals the number of monomers
-  per layer.
+  reported stacking distances near the R-$\pi$ value of 3.7 \AA. Headgroups in
+  our sandwiched initial configuration stack directly on top of each other while
+  headgroups in the parallel displaced initial configuration stack with an offset
+  of $180/nmon$ degrees where $nmon$ equals the number of monomers per layer. See
+  the Supplemental Information for a detailed illustration of the initial
+  configurations in each mode.
 
@@
 
+  \subsubsection{\textit{Determining equilibration time}}
+
   Using equilibrated structures, we carry out various calculations to
@@
 
+  \subsubsection{\textit{Calculation of pore spacing}}
+
   To calculate the equilibrated pore spacing, we measured the distance between
@@
 
-  To quantify the degree of layering and the equilibrium distance between layers
-  in our system, we calculate a spatial correlation function, $g(z)$, measured
-  along the z-axis (perpendicular to the membrane plane). To calculate $g(z)$,
-  we binned the z-component distances between the center of mass of each
-  component and all others of the same pore over at least 50 ns of equilibrated
-  trajectory and then normalized by the average number density. To extract the
-  average distance between layers we applied a discrete Fourier transform to
-  $g(z)$ and extracted the highest intensity frequency.
-
+  \subsubsection{\textit{Pair distribution functions}}
+
+  The normalized pair distribution function, $g(\mathbf{r})$, describes
+  the probability of finding a pair of particles separated by $\mathbf{r}$,
+  \begin{equation}
+	g(\mathbf{r})= \frac{1}{\rho N} \Bigg \langle \sum_{i=1}^{N}\sum_{j\neq i}^{N} \delta(\mathbf{r}+\mathbf{r_j}-\mathbf{r_i}) \Bigg \rangle
+	\label{eqn:correlation}
+  \end{equation}
+  where $\rho$ is the average number density of particles and $\delta(\mathbf{r})$
+  is the Dirac delta function\cite{kuriabova_linear_2010}. We applied equation 
+  \ref{eqn:correlation} in one and two dimensions to learn about various spatial
+  correlation functions.
+
+  In the 1D case, we measured the pair correlation function between centers of
+  masses of aromatic head group rings, $g(z)$, along the z-axis (perpendicular to
+  the membrane plane). To extract the average distance between layers we applied
+  a discrete Fourier transform to $g(z)$ and extracted the highest intensity
+  frequency.
+
+  We looked at the xy and xz pair distribution functions based on the center of
+  masses of the aromatic head group rings. We gave special consideration to the
+  xy cross-sections since there are multiple rings in the same plane at different
+  vertices of a polygon. We used a rotated frame of reference to avoid
+  ambiguities in the final pair distribution functions. For a given center of
+  mass, we rotated the coordinates so that the vector created from the center of
+  mass to the pore center was in line with the positive x axis.
+
+  \subsubsection{\textit{Simulated structure factor calculations}}
   % BJC: To be replaced by Joe's description
@@
   chains. Using a Fourier transform of $g(z)$, we see that sandwiched
-  configuration layers stack 4.39 \angstrom~apart while parallel displaced
-  configuration layers stack 4.38 \angstrom~apart.
+  configuration layers stack 4.39 \AA~apart while parallel displaced
+  configuration layers stack 4.38 \AA~apart.
 

### 2018-01-26 Ben_Manuscripts/structure_paper/supplemental.tex
new figures, better intro and more organization

@@
 	\texttt{antechamber}~\cite{wang_automatic_2006} using the AM1-BCC charge model.
-	The net charge on the monomer is input as -1 since the sodium ion we keep it as
+	The net charge on the monomer is input as -1 since the sodium ion is kept as 
 	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools_nodate} and the
@@
 	tutorial can be accessed elsewhere \cite{walker_antechamber_nodate}.
-	\item \textit{Create gromacs topologies from Amber output} : The output
+	\item \textit{Create GROMACS topologies from Amber output} : The output
 	of \texttt{LEaP} is a .inpcrd and a .prmtop file which are Amber topology
@@
 	simulated annealing procedure. We linearly decreased the temperature of the
-	system from 1000K to 50K over the course of 10 ns. We randomly chose a monomer
+	system from 1000 K to 50 K over the course of 10 ns. We randomly chose a monomer
 	configuration from the last 10 \% of the trajectory. 
@@
   \end{enumerate}
+
+  \begin{figure}
+	\centering
+        \includegraphics[width=0.9\textwidth]{monomer.png}
+	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
+		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
+		the blue atom is sodium.}\label{fig:monomer}
+  \end{figure}
+
+  \begin{figure}
+	\centering
+        \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
+	\caption{The groups used for $g(z)$ calculations. Red atoms are in the
+		tails group. Green atoms are in the head group region. The blue atom is sodium. 
+		}\label{fig:monomer_color_coded}
+  \end{figure}
 
@@
 	\centering
-        \includegraphics[width=0.9\textwidth]{monomer.png}
-	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
-		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
-		the blue atom is sodium.}\label{fig:monomer}
-  \end{figure}
-
-  \begin{figure}
-	\centering
-        \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
-	\caption{The groups used for $g(z)$ calculations. Red atoms are in the
-		tails group. Green atoms are in the head group region. The blue atom is sodium. 
-		}\label{fig:monomer_color_coded}
-  \end{figure}
-
-  \begin{figure}
-	\centering
 	\includegraphics[width=0.8\textwidth]{pore_radius_illustration.png}
@@
 
+  \noindent
+  \begingroup
+        \fontsize{14pt}{14pt}\selectfont
 	\textbf{Calculation of pore-to-pore spacing statistics}
+  \endgroup
 
+  \vspace{1em} 
   We are interested in 5 pore-to-pore distances which should all be

### 2018-02-01 Ben_Manuscripts/structure_paper/Draft.tex
New figures and edits

@@
 
-  %BJC: TODO: reproduce figure in latex (or gimp?) with higher resolution arrows
   \begin{figure}
@@
 
+  \subsubsection{\textit{The nematic order parameter}}
+
+  We calculated the nematic order parameter for our system in order to
+  understand the degree of ordering among monomer head groups. Typically, the
+  nematic order parameter is calculated for nematic liquid crystal systems which
+  are characterized by unidirectional ordering of liquid crystal monomers. The
+  preferred direction of monomers is defined by the unit director vector,
+  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
+  order parameter, $S$, is defined as:
+  \begin{equation}
+	 S = \frac{1}{2} \langle(3cos^2\theta -1)\rangle
+	\label{eqn:nematic_order_parameter}
+  \end{equation}
+  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
+  In a perfectly ordered system, the molecular axis should be aligned with
+  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
+  quantifying the degree of monomer head group alignment between systems. We use
+  Equation~\ref{eqn:nematic_order_parameter} to accomplish this by defining
+  $\mathbf{n}$ as the z-axis, or pore axis, and then measuring the angles,
+  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
+  the aromatic head groups. See the supplemental information for a diagram.
+
   \subsubsection{\textit{Pair distribution functions}}
@@
   \end{equation}
-  where $\rho$ is the average number density of particles and $\delta(\mathbf{r})$
-  is the Dirac delta function\cite{kuriabova_linear_2010}. We applied equation 
-  \ref{eqn:correlation} in one and two dimensions to learn about various spatial
-  correlation functions.
-
-  In the 1D case, we measured the pair correlation function between centers of
+  where $\rho$ is the average number density of particles and
+  $\delta(\mathbf{r})$ is the Dirac delta function\cite{kuriabova_linear_2010}.
+  We applied equation \ref{eqn:correlation} in three dimensions and then
+  extracted one and two dimensional distribution functions by collapsing the grid
+  along the appropropriate axes.
+
+  In the 1D case, we measured the pair distribution function between centers of
   masses of aromatic head group rings, $g(z)$, along the z-axis (perpendicular to
@@
 
-  We looked at the xy and xz pair distribution functions based on the center of
-  masses of the aromatic head group rings. We gave special consideration to the
-  xy cross-sections since there are multiple rings in the same plane at different
-  vertices of a polygon. We used a rotated frame of reference to avoid
-  ambiguities in the final pair distribution functions. For a given center of
-  mass, we rotated the coordinates so that the vector created from the center of
-  mass to the pore center was in line with the positive x axis.
+  In two dimensions, we observed xy and xz pair distribution functions based on
+  the center of masses of the aromatic head group rings. We gave special
+  consideration to the xy cross-sections since multiple rings exist in the same
+  plane located at different vertices of a polygon. We used a rotated frame of
+  reference to avoid ambiguity in the final pair distribution functions. For a
+  given center of mass, we rotated the coordinates so that the vector created
+  from the center of mass to the pore center was in line with the positive
+  x-axis.
+
+  \subsubsection{\textit{Radial distribution functions}}
+  Closely related to the spatial correlation functions, we explored the pores'
+  compositions by measuring the average number densities of various monomer
+  components as a function of distance from the pore centers. We looked at the
+  average number density of sodium ions, aromatic rings and carbon atoms making
+  up the monomer tails. We binned the radial distance of all atoms in each group
+  from the pore centers, then normalized by the volume of the annulus defined by
+  the bin edges and the z box vector.
 
@@
 
-  % BJC: I think this figure belongs somewhere else 
-%MRS4: yeah, probably. Possibly supplemental information.
-%  \begin{figure}
-%	\centering
-%	\begin{subfigure}[b]{0.32\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{sandwiched.png}
-%		\caption{}\label{fig:sandwiched}
-%	\end{subfigure}
-%	\begin{subfigure}[b]{0.32\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{PD.png}
-%		\caption{}\label{fig:pd}
-%	\end{subfigure}
-%	\begin{subfigure}[b]{0.32\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{Tshaped.png}
-%		\caption{}\label{fig:tshaped}
-%	\end{subfigure}
-%	\vskip\baselineskip
-%	\begin{subfigure}[b]{0.475\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{sandwichedlayers.png}
-%		\caption{}\label{fig:sandwichedlayers}
-%	\end{subfigure}
-%	\begin{subfigure}[b]{0.475\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{offsetlayers.png}
-%		\caption{}\label{fig:offsetlayers}
-%	\end{subfigure}
-%	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
-%	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
-%	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
-%	configuration }\label{fig:stacking}
-%  \end{figure}
-
-  We explored the pore composition by measuring the average number densities of
-  various monomer components as a function of distance from the pore centers. We
-  looked at the average number density of sodium ions, aromatic rings and carbon
-  atoms making up the monomer tails. We binned the radial distance of all atoms
-  in each group from the pore centers, then normalized by the volume of the
-  annulus defined by the bin edges and z box vector.
-  %BJC: Maybe write an equation here? It's hard to say precisely how I did it
-  %in words without it sounding confusing
+  \subsubsection{\textit{Ionic conductivity calculations}}
 
   We calculated ionic conductivity using two different methods for robustness.
-  The Nernst-Einstein relation relates the DC ionic conductivity to ion
+  The Nernst-Einstein relation, relates the DC ionic conductivity, $\sigma$, to ion
   diffusivity, $D$, concentration, $C$, ion charge, $q$, the Boltzmann constant,
-  $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$ 
+  $k_b$, and temperature, $T$: 
+  \begin{equation}
+	\sigma = \dfrac{q^2CD}{k_b T} 
+	\label{eqn:nernst_einstein}
+  \end{equation}
   We measured sodium ion diffusion coefficients by calculating the slope
@@
   of charge of the system. The conductance, $\gamma$, of the system can be
-  calculated as: $$ \gamma = \dfrac{D_Q}{k_b T} $$ We convert the resulting value
-  to ionic conductivity by multiplying by channel length and dividing by the
-  membrane cross sectional area. $D_Q$ is the diffusion coefficient of the
-  collective variable Q. It is calculated using the Einstein relation. One can
-  access a full derivation of the model elsewhere \cite{liu_collective_2013}.
+  calculated as:
+  \begin{equation}
+	 \gamma = \dfrac{D_Q}{k_b T} 
+	\label{eqn:collective_diffusion}
+  \end{equation}
+  We convert the resulting value to ionic conductivity by multiplying by
+  channel length and dividing by the membrane cross sectional area. $D_Q$ is the
+  diffusion coefficient of the collective variable Q. It is calculated using the
+  Einstein relation. One can access a detailed derivation of the model elsewhere
+  \cite{liu_collective_2013}.
 
@@
 
-  \subsection{Determining the Number of Monomers per Layer}
+  \subsection{Structural Characterization}
+  \subsubsection{Number of monomer per layer}
 
@@
   the measured equilibrated pore-to-pore distances. To discern the composition of
-  the monomer layers, addressing (\ref{point:monomernum}), we ran simulations of
-  systems created with 4 - 8 monomers per layer. We built systems in both the
-  parallel displaced and sandwiched configurations with layers initially spaced
-  3.7 \AA~apart. We prepared equilibrated configurations according to the dry
-  equilibration procedure. All systems are stable after 400 ns of simulation. In
-  a sense, all systems are at least metastable, addressing
-  (\ref{point:metastable}), however not all will make physical sense or fit the
-  experimental profile that we are looking to match. Figure~\ref{fig:p2p} shows
-  the pore spacing for all systems tested. Systems built with 5 monomers in each
-  layer equilibrate to a pore spacing that is most consistent with the
+  the monomer layers, addressing Question (\ref{point:monomernum}), we ran
+  simulations of systems created with 4 - 8 monomers per layer. We built systems
+  in both the parallel displaced and sandwiched configurations with layers
+  initially spaced 3.7 \AA~apart. We prepared equilibrated configurations
+  according to the dry equilibration procedure. All systems are stable after 400
+  ns of simulation. In a sense, all systems are at least metastable, addressing
+  Question (\ref{point:metastable}), however not all will make physical sense or fit
+  the experimental profile that we are looking to match. Figure~\ref{fig:p2p}
+  shows the pore spacing for all systems tested. Systems built with 5 monomers in
+  each layer equilibrate to a pore spacing that is most consistent with the
   experimental value of 4.12 nm derived from SAXS measurements
@@
 		increases as the number of monomers in each layer increases. The pore spacing
-		of systems starting in the sandwiched configuration is systematically slightly
+		of systems starting in the sandwiched configuration is systematically 
 		lower than those started in the parallel displaced configuration.}~\label{fig:p2p}
@@
 
-  \subsection{Layer partitioning}
-
-  We learned that layers are well-defined and persistent, answering
-  (\ref{point:layers}). We established our conclusion by plotting the one dimensional pair
-  distribution function, $g(z)$, calculated between atoms along the length of the
-  pores (Fig.~\ref{fig:zdf}). We measured $g(z)$ with respect to aromatic rings in
-  the head groups and, separately, with respect to carbon atoms in the alkane
-  chains. Using a Fourier transform of $g(z)$, we see that sandwiched
-  configuration layers stack 4.39 \AA~apart while parallel displaced
-  configuration layers stack 4.38 \AA~apart.
-
-  Insert paragraph about 2D pair distribution function (yz cross section).
-
-  We measured the correlation length, L, by fitting a function of the form:
-  $$1 + Asin(Bx + C)e^{-z/L}$$ where z is the independent variable and all
-  other variables are fitting parameters. The correlation length for each
-  system is given in Table~\ref{fig:correlation_length}.
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  System & Layer Separation & Correlation Length \\
-  \midrule
-  Sandwiched & 4.39 \AA & 41 $\pm$ 3 \AA \\
-  Parallel Displaced & 4.38 \AA & 86 $\pm$ 14 \AA \\
-  Experiment* & 3.7 \AA & 32 $\pm$ 1 \AA \\  
-  \bottomrule
-  \end{tabular}
-  \caption{*See supplemental information for derivation of experimental correlation length}~\label{fig:correlation_length}
-  \end{table}
-
-  %BJC: TODO: increase font size on legends
-  \begin{figure}
-        \centering
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
-                \caption{}\label{fig:zdf_layered}
-        \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
-                \caption{}\label{fig:zdf_offset}
-        \end{subfigure}
-	\caption{We support the existence of layers with the observance of
-		clear periodic maxima in the $z$-direction pair distribution functions of the
-		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
-		displaced configurations. The extent to which we consider a system to be
-		layered is based on the magnitude of the deviation of the periodic maxima from
-		the average number density. The sandwiched configuration possesses a higher
-		degree of layering than the parallel displaced configuration and, in both
-		cases, the head group region has a higher degree of layer partitioning than the
-		tail region. (See supplemental information for detailed definitions of the head
-		group and tail regions)}\label{fig:zdf}
-  \end{figure}
-
-  \subsection{Determination of Relative Interlayer Head Group Orientation}
-
-  We answer question (\ref{point:orientation}) by simulating X-ray diffraction
+  \subsubsection{Relative interlayer head group orientation}
+
+  We answer Question (\ref{point:orientation}) by simulating X-ray diffraction
   patterns produced from equilibrated MD trajectories. We tested systems built
@@
   \includegraphics[width=0.5\linewidth]{tilt_dist.png}
-  \caption{We measured the angle made between each monomer alkane tail and the membrane plane. 
-  The average tilt angle is near 7\degree~which is far from the 37\degree~tilt angle 
-  previously used to explain R-spots.}~\label{fig:tilt}
+  \caption{We measured the angle made between each monomer alkane tail and the
+	  membrane plane. The average tilt angle is near 7\degree~which is far from the
+	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
   \end{figure}
@@
 
-  \subsection{Initial Layer Spacing Affects System Equilibration}
-
-%MRS4: can we come up with another name?
-I still think disordered pores is a decent name, since there is no pi-stacking layering.
-``structures that form when layers are 5 AA apart'' is not so good.
-or ``more disordered''?
-%BJC3: agreed, I'll stick with disordered pores
-%  The $z$-direction correlation functions show that layers in our model prefer
-%  to stack further apart than 3.7 \angstrom~as suggested by experiment.
+  \subsubsection{Layer partitioning}
+
+  We learned that layers are well-defined and persistent, answering Question
+  (\ref{point:layers}). We established our conclusion by plotting the two
+  dimensional pair distribution function, $g(y,z)$ of head group phenyl rings
+  using Equation~\ref{eqn:correlation} (Figure \ref{fig:yz_correlation}). In both
+  configurations, the phenyl rings stack in the z-direction, along $y=0$, and
+  clear layers are formed. The layers in the sandwiched configuration are more
+  defined than those in the parallel displaced configuration and are strongly
+  correlated with adjacent layers. We also observe correlation of layers between
+  pores indicated by the non uniformity in $g(y,z)$ in adjacent columns (along $y
+  = \pm 3.65$).Parallel displaced layers display weaker correlations but do not
+  decay in their intensity as z increases. We do not see correlation between
+  pores, however correlations within pores are strong throughout the length of
+  the unit cell since there is no noticeable decay in layer intensity.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{layered_yz_correlation.png}
+	\caption{}\label{fig:layered_yz_correlation}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{offset_yz_correlation.png}
+        \caption{}\label{fig:offset_yz_correlation}
+  \end{subfigure}
+  \caption{2D pair distribution functions generated from systems built in the 
+	   sandwiched (a) and parallel displaced (b) configurations, provide
+           a more detailed picture of the pore structure in each. The sandwiched
+	   configuration}\label{fig:yz_correlation}
+  \end{figure}
+
+  We plotted the one-dimensional pair distribution function, $g(z)$, for the
+  phenyl rings and for carbon atoms that make up the monomer tails (Figure
+  \ref{fig:zdf}). The plots show clear periodic maxima where layers are present.
+  Layering is most pronounced in the head group region, however there is still a
+  degree of layering that persists into the tail region. Using a Fourier
+  transform on $g(z)$ from the head groups, we see that sandwiched configuration
+  layers stack 4.39 \AA~apart while parallel displaced configuration layers stack
+  4.38 \AA~apart. Both stacking distances are in agreement with those observed
+  in the simulated XRD patterns.
+
+  \begin{figure}
+        \centering
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
+                \caption{}\label{fig:zdf_layered}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
+                \caption{}\label{fig:zdf_offset}
+        \end{subfigure}
+	\caption{We support the existence of layers with the observance of
+		clear periodic maxima in the $z$-direction pair distribution functions of the
+		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
+		displaced configurations. The extent to which we consider a system to be
+		layered is based on the magnitude of the deviation of the periodic maxima from
+		the average number density. The sandwiched configuration possesses a higher
+		degree of layering than the parallel displaced configuration and, in both
+		cases, the head group region has a higher degree of layer partitioning than the
+		tail region. (See supplemental information for detailed definitions of the head
+		group and tail regions)}\label{fig:zdf}
+  \end{figure}
+
+  \subsubsection{Initial Layer Spacing Affects System Equilibration}
+
+  All systems up to this point were built with layers stacked 3.7 \AA~apart.
   When we build systems with layers stacked 5.0 \AA~apart and then let them
@@
   configuration, suggesting that we have found another metastable free energy
-  basin, further corroborating (\ref{point:metastable}). The basins are
-  differentiated by their relative degrees of ordering resulting from different
-  spatial arrangements.
-
-  We expect that the head groups in more ordered systems will be predominantly
-  coplanar with the xy plane. We defined a director vector, \textbf{n}, as the
-  vector normal to the plane of the monomer's aromatic head group, then measured
-  the distribution of angles between it and the z-axis. We used the resulting
-  distibution of angles to calculate the nematic order parameter, S. The values
-  of S for systems resulting from each initial configuration are presented in
-  Table \ref{table:nematic}. The full distributions of angles between \textbf{n}
-  and the z-axis are presented in the supplemental material. In general, systems
-  started with layers spaced 3.7 \AA apart are more nematically ordered than
-  those initially spaced 5 \AA apart. We will refer to systems built with layers
-  initially spaced 3.7 \AA apart and 5.0 \AA apart as the ordered and disordered
-  pore basins respectively. We studied each basin in both the parallel displaced
-  and sandwiched configurations.
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{cc}
-  \toprule
-  System & Nematic Order Parameter (S) \\
-  \midrule
-  Sandwiched, Ordered & 0.659 $\pm$ 0.003 \\
-  Parallel Displaced, Ordered & 0.601 $\pm$ 0.003 \\
-  Sandwiched, Disordered & 0.565 $\pm$ 0.002 \\
-  Parallel Displaced, Disordered & 0.503 $\pm$ 0.002 \\
-  \bottomrule
-  \end{tabular}
-  \caption{The nematic order parameter is higher when layers are initially spaced
-  3.7 \AA apart. A perfectly stacked system with aromatic rings coplanar with the
-  xy plane would have a nematic order parameter of 1, while isotropically aligned
-  director vectors would have a nematic order parameter of 0.}~\label{table:nematic}
-  \end{table}
-
-  We observe more evidence of disorder in the disordered pore basin when we 
-  plot the two dimensional pair distribution function between the centers of 
-  mass of monomer head groups. ADD MORE ANALYSIS ONCE CODE IS WORKING HOW I WANT IT
-
-  \begin{figure}
-  \begin{subfigure}{1\linewidth}
-        \centering
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{layered_xy_rings.png}
-                \caption{}~\label{fig:sandwich_xy}
-        \end{subfigure}%
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{offset_xy_rings.png}
-                \caption{}~\label{fig:offset_xy}
-        \end{subfigure}
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{disorder_sandwich_xy_rings.png}
-                \caption{}~\label{fig:disorder_sandwich_xy}
-        \end{subfigure}%
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{disorder_offset_xy_rings.png}
-                \caption{}~\label{fig:disorder_offset_xy}
-        \end{subfigure}
-  \end{subfigure}
-  \caption{}\label{fig:xy_correlation}
-  \end{figure}
+  basin, further corroborating Question (\ref{point:metastable}). 
+  %The basins are
+  %differentiated by their relative degrees of ordering resulting from different
+  %spatial arrangements. 
+  For reasons we will develop in the next segment of our
+  discussion, configurations intially built with layers stacked 5.0 \AA~apart 
+  will be grouped into the disordered pore basin, while those built with layers
+  initially stacked 3.7 \AA~apart will be grouped into the ordered basin.
+
+  The equilibrated pore spacing and distance between layers are different in
+  the disordered pore basin. For both head group stacking arrangements, we
+  observe an increase in the equilibrated distance between layers
+  (Fig.~\ref{fig:dbwl_disordered}) and a corresponding decrease in pore spacing
+  (Fig.~\ref{fig:p2p_disordered}).
 
@@
   differences. In the parallel displaced configuration, almost all contrast
-  between R-spots and R-alkanes fades (Fig.~\ref{fig:offset_disordered_xrd}). In
-  the sandwiched configuration, R-spots is weakly present, but in different
+  between R-spots and R-alkanes fades (Figure~\ref{fig:offset_disordered_xrd}).
+  In the sandwiched configuration, R-spots is weakly present, but in different
   locations, showing higher intensity at the top and bottom of the pattern as
-  well as at the intersection of R-alkanes with q$_z$ = 0 (Fig.
-  ~\ref{fig:layered_disordered_xrd}).
-
-  The sandwiched and parallel displaced assemblies do not deviate from their
-  initial head group arrangement. R-helix is still faintly visible in the
-  parallel displaced configuration and is absent in the sandwiched simulated
-  diffraction pattern. The spectroscopic signatures are unique to the two
-  different head group configurations.
-
-  The equilibrated pore spacing and distance between layers are different in
-  the disordered pore basin. For both head group stacking arrangements, we
-  observe a decrease in pore spacing (Fig.~\ref{fig:p2p_disordered}) and a
-  corresponding increase in the equilibrated distance between layers
-  (Fig.~\ref{fig:dbwl_disordered}).
+  well as at the intersection of R-alkanes with q$_z$ = 0
+  (Figure~\ref{fig:layered_disordered_xrd}).
+
+% BJC: in the interest of being concise, I leave this out for now.
+%  The sandwiched and parallel displaced assemblies do not deviate from their
+%  initial head group arrangement. R-helix is still faintly visible in the
+%  parallel displaced configuration and is absent in the sandwiched simulated
+%  diffraction pattern. The spectroscopic signatures are unique to the two
+%  different head group configurations.
 
@@
 
-  \subsection{Pore Composition Depends on Initial Configuration}
+  %BJC: this may belong in methods, but I think it might fit here because it
+  % gives context for the choice of functional form to fit
+
+  We quantified order in the z-direction by measuring the correlation lengths
+  of all configurations. We measured the correlation length, L, by fitting $g(z)$
+  using a non-linear least squares algorithm subject to a function of the form:
+  \begin{equation}
+  	1 + Asin(Bx + C)e^{-z/L}
+        \label{eqn:correlation_fit}
+  \end{equation}
+  where z is the independent variable and all other variables are fitting
+  parameters. The correlation length for each system is given in
+  Table~\ref{table:nematic}.
+
+  Correlation lengths are shorter in the disordered pore basin than in the
+  ordered pore basin. Layers in the ordered pore basin are strongly correlated
+  with neighboring layers up to more than 10 layers away. This behavior deviates
+  from experimental evidence. The experimental correlation length suggests that
+  layers are correlated with about 3 neighboring layers which is closer to the
+  values exhibited by the disordered pore basin. We may need to simulate a system
+  with many more layers in order to reduce the correlation contributed by
+  periodic copies of the system.
+
+% BJC: below is summarized in methods
+%  We expect that the head groups in more ordered systems will be predominantly
+%  coplanar with the xy plane. We defined a director vector, \textbf{n}, as the
+%  vector normal to the plane of the monomer's aromatic head group, then measured
+%  the distribution of angles between it and the z-axis. We used the resulting
+%  distibution of angles to calculate the nematic order parameter, S. 
+  We calculated the nematic order parameter for each system using Equation
+  \ref{eqn:nematic_order_parameter}. The calculated values of S are presented in
+  Table \ref{table:nematic}. The full distributions of angles between director
+  \textbf{n} and vectors orthogonal to monomer phenyl rings are presented in the
+  supplemental material. In general, ordered pore basin systems are more
+  nematically ordered than disordered pore basin systems. The head groups of the
+  disordered pore basin have more rotational freedom about the xy plane likely
+  due to the larger separation between layers.
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{ccc}
+  \toprule
+  System & Correlation Length (\AA) & Nematic Order Parameter (S) \\
+  \midrule
+  Sandwiched, Ordered & 41 $\pm$ 3 & 0.659 $\pm$ 0.003 \\
+  Parallel Displaced, Ordered & 86 $\pm$ 14 & 0.601 $\pm$ 0.003 \\
+  Sandwiched, Disordered & 17 $\pm$ 3 & 0.565 $\pm$ 0.002 \\
+  Parallel Displaced, Disordered & 9 $\pm$ 1 & 0.503 $\pm$ 0.002 \\
+  Experiment & 10 $\pm$ 1 & -- \\
+  \bottomrule
+  \end{tabular}
+  \caption{The nematic order parameter, S, is higher when layers are initially spaced
+  3.7 \AA apart. In general, the sandwiched configuration has higher nematic order
+  than the parallel displaced configuration. Correlation lengths are higher in
+  the ordered pore basin. Correlation lengths in the disordered pore basin are
+  in closer agreement with experiment.}~\label{table:nematic}
+  \end{table}
+
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{ccc}
+%  \toprule
+%  System & Layer Separation & Correlation Length \\
+%  \midrule
+%  Sandwiched & 4.39 \AA & 41 $\pm$ 3 \AA \\
+%  Parallel Displaced & 4.38 \AA & 86 $\pm$ 14 \AA \\
+%  Experiment* & 3.7 \AA & 10 $\pm$ 1 \AA \\  
+%  \bottomrule
+%  \end{tabular}
+%  \caption{Uncertainties are derived from the diagonal entries in the
+%	  covariance matrix calculated from a non-linear least squares fit to the data.
+%	  *See supplemental information for derivation of experimental correlation
+%	  length}~\label{table:correlation_length}
+%  \end{table}
+
+  We observe evidence of disorder in the xy plane of the disordered pore basin when
+  we plot the two dimensional pair distribution function, $g(x,y)$, between the
+  centers of mass of monomer phenyl rings (Figure \ref{fig:xy_correlation}). The
+  difference is most apparent in the plots of the sandwiched configurations. In
+  the ordered pore basin, head groups primarily stay stacked on top of each other
+  while in the disordered pore basin, head groups exhibit more motion about the pore
+  center and even drift into the middle of the pore. $g(x,y)$ for the parallel displaced
+  configuration is less informative since adjacent layers are displaced in a way that
+  occupies the gaps that are seen in $g(x,y)$ for the sandwiched configuration
+
+  \begin{figure}
+  \begin{subfigure}{1\linewidth}
+        \centering
+        \begin{subfigure}{0.47\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{layered_xy_correlation.png}
+                \caption{Sandwiched, Ordered Pore Basin}~\label{fig:sandwich_xy}
+        \end{subfigure}%
+        \begin{subfigure}{0.47\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{offset_xy_correlation.png}
+                \caption{Parallel Displaced, Ordered Pore Basin}~\label{fig:offset_xy}
+        \end{subfigure}
+        \begin{subfigure}{0.47\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{disorder_xy_correlation.png}
+                \caption{Sandwiched, Disordered Pore Basin}~\label{fig:disorder_sandwich_xy_correlation}
+        \end{subfigure}%
+        \begin{subfigure}{0.47\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{disorder_offset_xy_correlation.png}
+                \caption{Parallel Displaced, Disordered Pore Basin}~\label{fig:disorder_offset_xy_correlation}
+        \end{subfigure}
+  \end{subfigure}
+  \caption{$g(x,y)$ for sandwiched and parallel displaced configurations in the
+	  ordered and disordered pore basins illustrate disorder present in the xy plane
+	  when initial configuration layers are stacked 5\AA
+	  apart.}\label{fig:xy_correlation}
+  \end{figure}
+
+  \subsubsection{Chemical composition of pore columns}
 
@@
   In all cases, the space in the pore region is filled with sodium ions and
-  head groups. In the ordered pore systems, there is less density in the center of
-  the pore indicating a more ordered pore structure. In both the sandwiched and
-  parallel displaced configurations, we see the density of head groups and sodium
-  ions fall to less than 50\% of its maximum at r = 0
-  (Fig.~\ref{fig:layered_density}). The situation is most pronounced in the
-  sandwiched configuration where the maximum head group density occurs 0.44 nm
-  from the pore center. The parallel displaced configuration reaches its maximum
-  0.35 nm from the pore center. In contrast, both disordered pore systems show
-  very little difference in density from its maximum. This implies a more uniform
-  distribution of head groups within the pore center. 
+  head groups. Systems in the ordered pore basin are less dense in
+  the center of the pore. In both the sandwiched and parallel displaced
+  configurations, we see the density of head groups and sodium ions fall to less
+  than 50\% of its maximum at r = 0 (Fig.~\ref{fig:layered_density}). The
+  situation is most pronounced in the sandwiched configuration where the maximum
+  head group density occurs 0.44 nm from the pore center. The parallel displaced
+  configuration reaches its maximum 0.35 nm from the pore center. In contrast,
+  both disordered pore systems show very little difference in density from its
+  maximum. This implies a more uniform distribution of head groups within the
+  pore center. 
   % High vacancy is less likely to be stable in the real system
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.47\textwidth}
         \includegraphics[width=1\linewidth]{offset_density.png}
-        \caption{Parallel displaced, 3.7 \AA~initial layer spacing}
+        \caption{Parallel Displaced, Ordered Pore Basin}
         \label{fig:offset_density}
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.47\textwidth}
         \includegraphics[width=1\linewidth]{layered_density.png}
-        \caption{Sandwiched, 3.7 \AA~initial layer spacing}
+        \caption{Sandwiched, Ordered Pore Basin}
         \label{fig:layered_density}
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.47\textwidth}
         \includegraphics[width=1\linewidth]{disordered_offset_density.png}
-        \caption{Parallel displaced, 5 \AA~initial layer spacing}
+        \caption{Parallel Displaced, Disorderd Pore Basin}
         \label{fig:disordered_offset_density}
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.47\textwidth}
         \includegraphics[width=1\linewidth]{disordered_density.png}
-        \caption{Sandwiched, 5 \AA~initial layer spacing}
+        \caption{Sandwiched, Disordered Pore Basin}
         \label{fig:disorder_layered_density}
@@
 
-  In all cases, water disrupts structuring of the model \ref{fig:solvation}.
-  When we add water to the system, the intensity of the reflections decrease. In
-  systems built with 5 wt\% water, R-$\pi$ and R-spots become nearly
-  indistinguishable from R-alkanes.
+  In all cases, water disrupts structuring of the model.  When we add water to
+  the system, the intensity of the reflections decrease. In systems built with 5
+  wt\% water, R-$\pi$ and R-spots become nearly indistinguishable from R-alkanes.
+
+  In systems built with 5 wt\% water, the pore region becomes filled with
+  water. We plotted the number density of components in this system. As with the 
+  dry systems, we see a gradual compositional transition from hydrophilic to hydrophobic.  
+  We see that the pores become a mixture of water molecules and sodium ions (Fig.
+  \ref{fig:water_density}).
+
+  The membrane swells when we introduce water. The location of maximum head
+  group density shifts from 0.35 to 0.62 nm and from 0.44 to 0.61 nm in the
+  parallel displaced and sandwiched configurations respectively. Again, we
+  observe the existence of ions, head groups and water outside the pore region,
+  however in the hydrated system, the head groups drift beyond 1.5 \AA~from the
+  pore center. In the dry systems, head groups did not wander beyond 1.4 \AA~from
+  the pore center. Both observations suggest that water pushes all components
+  radially outward from the pore center, characteristic of a swelling process.  
+  This system is a closer representation of the H\textsubscript{II} phase which
+  is typically synthesized with ca. 8 wt\% water. Further investigation of
+  hydrated systems can help unravel the mechanisms for selective transport in
+  separations of aqueous solutions.
 
   % BJC: unsure where or if this paragraph fits
+  % BJC: Probably as the last paragraph of this section
   Water is not necessary to maintain an ordered pore structure. We do not
@@
 
-  In systems built with 5 wt\% water, the pore region becomes filled with
-  water. We plotted the number density of components in this system. As with the 
-  dry systems, we see a gradual compositional transition from hydrophilic to hydrophobic.  
-  We see that the pores become a mixture of water molecules and sodium ions (Fig.
-  \ref{fig:water_density}).
-
-  The membrane swells when we introduce water. The location of maximum head
-  group density shifts from 0.35 to 0.62 nm and from 0.44 to 0.61 nm in the
-  parallel displaced and sandwiched configurations respectively. Again, we
-  observe the existence of ions, head groups and water outside the pore region,
-  however in the hydrated system, the head groups drift beyond 1.5 \AA~from the
-  pore center. In the dry systems, head groups did not wander beyond 1.4 \AA~from
-  the pore center. Both observations suggest that water pushes all components
-  radially outward from the pore center, characteristic of a swelling process.
-
-  This system is a closer representation of the H\textsubscript{II} phase which
-  is typically synthesized with ca. 8 wt\% water. Further investigation of
-  hydrated systems can help unravel the mechanisms for selective transport in
-  separations of aqueous solutions.
-
   \begin{figure}
@@
 
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{layered_xy_correlation.png}
+        \caption{Parallel Displaced, Ordered Pore Basin}
+        \label{fig:layered_xy_correlation_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{layered_solvated_xy_correlation.png}
+        \caption{Sandwiched, Ordered Pore Basin}
+        \label{fig:layered_solvated_xy_correlation}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{offset_xy_correlation.png}
+        \caption{Parallel Displaced, Disorderd Pore Basin}
+        \label{fig:offset_xy_correlation_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{offset_solvated_xy_correlation.png}
+        \caption{Sandwiched, Disordered Pore Basin}
+        \label{fig:offset_solvated_xy_correlation}
+  \end{subfigure}
+  \caption{}~\label{fig:solvated_correlation}
+  \end{figure}
+
   \subsection{Model Ionic Conductivity Measurements}
 
-  We used the equilibrated parallel displaced system to calculate ionic
+  We used the equilibrated ordered parallel displaced system to calculate ionic
   conductivity since its structure is the closest match to experiment. The model

### 2018-02-01 Ben_Manuscripts/structure_paper/supplemental.tex
New figures and edits

@@
 
+  \noindent
+  \begingroup
+        \fontsize{14pt}{14pt}\selectfont
+        \textbf{Crosslinking Mechanism}
+  \endgroup
+
+  Crosslinking of the the monomer Na-GA3C11 occurs by a UV initiated free
+  radical polymerization (Figure~\ref{fig:xlink_mech}).  Head-to-tail addition
+  takes place between terminal vinyl groups on each of the monomer tails.  We
+  only considered head-to-tail addition since it is the dominant propagation mode
+  in the real system.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{Crosslink_mechanism.eps}
+  \caption{Terminal vinyl groups present on each monomer tail react with free
+	  radical initiators to create monomers with terminal vinyl radicals.  Vinyl
+	  radicals react with the vinyl groups of other monomers in to propagate
+	  crosslinking.}\label{fig:xlink_mech}
+  \end{figure}
+
 \clearpage

### 2018-02-01 llclib/setup.py

@@ -2,5 +2,5 @@ from distutils.core import setup
 from Cython.Build import cythonize
 
 setup(
-    ext_modules = cythonize("physical.pyx")
+    ext_modules = cythonize("fast_rotate.pyx")
 )

### 2018-02-06 Ben_Manuscripts/structure_paper/supplemental.tex
got rid of thing

@@
 
+  \vspace{1em}
   \begingroup
 	\fontsize{14pt}{12pt}\selectfont
-	\textbf{Initial Configuration Dependence}
+	\textbf{Experimental correlation length of R-$\pi$}
   \endgroup
@@
   \vspace{1em}
-  We addressed any major dependence on initial configuration in the main text.
-  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
-  monomers per layer. We also showed that systems are stable when monomer head
-  groups are oriented in the parallel displaced and sandwiched configurations
-  (See Figure~\ref{fig:stacking}). Our model best supports a system built with 5
-  monomers per layer in the sandwiched configuration.
-
-  There are three other parameters whose choice may influence the equilibrium
-  structure: initial pore spacing, initial pore radius and initial distance
-  between layers. Here we show the results of a sensitivity analysis performed
-  on the three parameters. To reduce the size of the sensitivity analysis, we
-  only tested systems built with 5 monomers per layer with layers stacked in 
-  the parallel displaced configuration. We equilibrated all systems according
-  to the dry equilibration procedure.
-
-  \vspace{1em}
-  \begingroup
-	\fontsize{14pt}{12pt}\selectfont
-	\textbf{Experimental correlation length of Ri-$\pi$}
-  \endgroup
-
-  \vspace{1em}
-  Experimentalists did not measure the correlation length, so we estimated it from
-  the raw data. We took a slice of the 2D WAXS data along the dashed line in Figure
-  ~\ref{fig:waxs_dashed}. We removed background noise by subtracting
-  the intensity far from the pattern (high $q$) uniformly. We used a least squares
-  algorithm to fit a lorentzian curve to the data. Only values recorded above $q_z$ = 1.6 were considered for 
-  the fit in order to mitigate interference from R-alkanes (Figure~\ref{fig:correlation_length_exp}).
-  The full width at half maximum (FWHM) is related to the correlation length, L, by
-  the relationship: $ L = \frac{\pi}{FWHM} $. The error in the value is calculated
-  as the square root of the diagonal entry of the covariance matrix calculated 
+  Experimentalists did not measure the correlation length, so we estimated it
+  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
+  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
+  intensity far from the pattern (high $q$) uniformly. We used a least squares
+  algorithm to fit a lorentzian curve to the data. Only values recorded above
+  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
+  R-alkanes (Figure~\ref{fig:correlation_length_exp}).  The full width at half
+  maximum (FWHM) is related to the correlation length, L, by the relationship: $
+  L = \frac{\pi}{FWHM} $. The error in the value is calculated as the square root
+  of the diagonal entry of the covariance matrix calculated 
   % need citations and more on lorentzian parameters
@@
   %Our model is insensitive to initial configuration if monomer placement is chosen within reason. 
+  \begingroup
+	\fontsize{14pt}{12pt}\selectfont
+	\textbf{Initial Configuration Dependence}
+  \endgroup
+
+  \vspace{1em}
+  We addressed any major dependence on initial configuration in the main text.
+  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
+  monomers per layer. We also showed that systems are stable when monomer head
+  groups are oriented in the parallel displaced and sandwiched configurations
+  (See Figure~\ref{fig:stacking}). Our model is most consistent with experiment
+  when built with 5 monomers per layer, with layers stacked 3.7 \AA~apart in 
+  the parallel displaced configuration.
+
+  There are three other parameters whose choice may influence the equilibrium
+  structure: initial pore spacing, initial pore radius and initial distance
+  between layers. Here we show the results of a sensitivity analysis performed
+  on the three parameters. To reduce the size of the sensitivity analysis, we
+  only tested systems built with 5 monomers per layer with layers stacked in 
+  the parallel displaced configuration. We equilibrated all systems according
+  to the dry equilibration procedure.
 
@@
 	  We tested five different initial pore spacings, defined as the
-	  distance between the central axis of each pore with all others. To reduce the
-	  number of variables, we held the pore radius constant, at 6 \AA~and the
-	  distance between layers at 3.7 \AA~since those were the values used in our
-	  optimal system in the main text. If the initial pore spacing is chosen to be
-	  too small, pore columns abruptly repel each other as soon as they are able to
-	  overcome the restraining potential present as part of the dry equilibration
-	  procedure. We avoided using systems that exhibit this behavior since the
-	  behavior increases the chances of a system to become kinetically trapped in an
-	  undesired metastable free energy basin.
+	  distance between the central axis of each pore with all others
+	  (Figure~\ref{fig:p2p_diagram}). To reduce the number of variables, we held the
+	  pore radius constant, at 6 \AA~and the distance between layers at 3.7 \AA~since
+	  those were the values used in our optimal system in the main text. We
+	  prioritized ensuring that resulting configurations maintain the expected
+	  hexagonal symmetry. If initial pore spacing is too small, we observe repulsion
+	  between columns which disrupts equilibration. If the pore spacing is too large
+	  the pores squeeze together, but in a distorted hexagonal array because the xy
+	  translation of the pores is somewhat erratic.
+
+%	  If the initial pore spacing is chosen to be
+%	  too small, pore columns abruptly repel each other as soon as they are able to
+%	  overcome the restraining potential present as part of the dry equilibration
+%	  procedure. We avoided using systems that exhibit this behavior since the
+%	  behavior increases the chances of a system to become kinetically trapped in an
+%	  undesired metastable free energy basin.
 
@@
 
-	  	\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to have a test system
-		with an intial spacing below the experimental value. As soon as the restraining
-		potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the columns are able to
-		separate resulting in a large jump in pore spacing (Figure~\ref{fig:p2p_39}).
+		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
+		have a test system with an intial spacing below the experimental value. As soon
+		as the restraining potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the
+		columns are able to repel resulting in a large jump in pore spacing
+		(Figure~\ref{fig:p2p_39}). After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
+		There is a large uncertainty in this value because the 1-4 pore spacing
+		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
+		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
+		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
+                towards cubic packing.
 
@@
 		repulsion of columns once the restraining potential is switched to 56 KJ
-		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}).
+		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). After 400 ns, the
+		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
+		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
+		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
+		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
+		spacings is 3.96 nm.
 
-		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger than the
-		experimental value. We observe relatively stable pore spacing during the
-		restrained portion of the dry equilibration procedure
-		(Figure~\ref{fig:p2p_45}). We chose to use this value for all our simulations
-		in the main text.
+		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
+		than the experimental value. We observe relatively stable pore spacing during
+		the restrained portion of the dry equilibration procedure
+		(Figure~\ref{fig:p2p_45}). The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
+		The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
+		pore spacing. We chose to use this value for all our simulations in the main
+		text.
 
@@
 		nm$^{-2}$, the pore spacing begins to decrease linearly (Figure~\ref{fig:p2p_50}).
+		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm. There is a large
+                uncertainty with this value because, again, the array of pores deviates from 
+                hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
+                2 drifts outward from the array and forces the 1-4 distance to shrink in 
+                response.
 
@@
 		introduced unnecessarily. The system equilibrates to a pore spacing of 4.27
-		$\pm$ 0.06 nm.
+		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
+                spacing of 3.99 \AA~ which distorts the hexagonal array.
 
 	  \end{enumerate}
+
+	  \begin{figure}
+		\centering
+		\includegraphics[width=0.4\textwidth]{p2p_diagram.png}
+		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
+		equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
+		are the same.}~\label{fig:p2p_diagram}
+	  \end{figure}
 

### 2018-02-06 Ben_Manuscripts/structure_paper/Draft.tex

@@
   \begin{abstract}
-
+  %MRS5: Abstract can contain a little less introduction material. Suggest the following cuts  
   Nanostructured porous membranes made from the cross-linked hexagonal phase of
   self-assembled lyotropic liquid crystals (LLCs) are a promising material for
-  selective separations. To date, their separation performance has only been
-  characterized with membranes made from a small set of LLC monomers. There
-  remains a large design space that we can likely exploit to design membranes for
-  solute specific separations. In this work, we develop an atomistic molecular
+  selective separations. 
+  %To date, their separation performance has only been
+  %characterized with membranes made from a small set of LLC monomers. There
+  %remains a large design space that we can likely exploit to design membranes for
+  %solute specific separations. 
+  In this work, we develop an atomistic molecular
   model of an LLC membrane. We show that our model is maximally consistent with
@@
   We explore, in depth, the composition and structure of the nanopores in order
-  to give insights that are not easily accessible to experimentalists. With the
-  clear picture of the nanoscopic structure of these membranes gained from this
-  work, we will be able to use the model to understand the mechanisms of small
-  charged and uncharged solute transport within the nanopores, and eventually we
-  will be able to screen large sets of modified monomers with their separation
-  properties in mind.
+  to give insights that are not easily accessible to experimentalists. 
+  %MRS5: suggest:
+  %With the
+  %clear picture of the nanoscopic structure of these membranes gained from this
+  %work, we will be able to use the model to understand the mechanisms of small
+  %charged and uncharged solute transport within the nanopores, and eventually we
+  %will be able to screen large sets of modified monomers with their separation
+  %properties in mind.  
+  The clearer picture of the nanoscopic structure of these membranes provided in this study will enable better understanding of the mechanisms of small molecule transport within these nanopores.
 
@@
   \section{Introduction}
+
+%MRS5: want to get people engaged from the beginning. The first
+%paragraph should describe a problem to be solved. Then you can get
+%into the motivating details (like background of the alternatives, and
+%why we need something different).  I feel like this is an
+%introduction into different types of membranes, though it should be
+%an introduction to the problem that this paper takes steps towards
+%solving.
 
@@
   film composite (TFC) membranes with a porous support layer and a dense
-  crosslinked polymer active layer which near indiscriminately separates all
-  solutes. NF membranes have porous architectures with pores on the order of 1 nm
+  crosslinked polymer active layer which near indiscriminately 
+%MRS5: 
+%  Maybe ``impermeable to all solutes?'' or ``separates all solutes from water.''  As written, it's not stated what the solutes are separated from.
+  separates all solutes. 
+NF membranes have porous architectures with pores on the order of 1 nm
   in size which separate primarily based on solute size
@@
 
+%MRS5: a more compelling thesis is that we need membranes that are more selective than RO and NF.  
   RO and NF are finding applications beyond primarily water-based
@@
 
+%MRS5: under solution-diffusion, then the free energy to partition into the membrane is important as well, correct?
   Selective separation by a semipermeable membrane barrier is governed by two
@@
 
+%MRS5: maybe a more compelling thesis would be that LLC might have the capabilility to serve as selective membranes?
   Lyotropic liquid crystals (LLCs) are amphiphilic molecules that have the
@@
   membranes lack a pore size distribution, they inherently exhibit high
-  selectivity due to their strict molecular weight cut-off (MWCO).  Additionally,
-  the LLCs chosen to make membranes for this application are salts.  The membrane
+  selectivity due to their strict molecular weight cut-off (MWCO). 
+%MRS5: is there a citation for the strict MWCO? 
+%MRS5: suggested change.
+ Additionally, the LLCs chosen to make membranes for this application are salts, and therefore lead to 
+Donnan exclusion of ions in solution.
+ The membrane
   gains a net surface charge when counterions from head groups that line the pore
   walls escape into the feed solution in order to balance the gradients of
-  concentration and electric potential. This effect, which causes the membrane to
-  repel incoming charged species, is called Donnan exclusion
+  concentration and electric potential. 
+%This effect, which causes the membrane to
+%  repel incoming charged species, is called Donnan exclusion
+
   \cite{donnan_theory_1995}.
@@
   NaCl, Q\textsubscript{I} phase membrane filtration experiments have shown
-  selectivity 2-3 times higher than commercial RO and 6-12 times higher than
+%MRS5: for dashes between two numbers, use double -- for the correct length in the file. 
+  selectivity 2--3 times higher than commercial RO and 6--12 times higher than
   commercial NF membranes \cite{dischinger_application_2017}.  When separating a
@@
 
+%MRS5: be more explicit about current efforts. Also use the
+%opportunity of a thesis statement to convince the readership of
+%something.  what do you want to convince them?
   We will focus our current efforts around the H\textsubscript{II} phase since
   its geometry should give optimal transport performance compared to the
-  Q\textsubscript{I} phase. The H\textsubscript{II} phase forms at room
+  Q\textsubscript{I} phase. 
+%MRS5: citation on this above?
+  The H\textsubscript{II} phase forms at room
   temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
@@
   These hexagonal columnar phases represent the ideal geometry for membrane
-  transport. The most promising Q\textsubscript{I} phase for membrane
+  transport. 
+%MRS5: maybe less about Q_I since it's not in this paper?  The introduction should be an introduction to the paper.
+The most promising Q\textsubscript{I} phase for membrane
   applications forms at 70\degree C when monomer is mixed with c.a.~20 wt\%
@@
   \end{subfigure}
+%MRS5: not sure Q should be in here.
   \caption{The choice of LLC monomer leads to different favorable liquid
@@
 
+%MRS5: not a strong thesis.  Why has it been revived?  The reasons for that would be a better thesis.
   Research into the H\textsubscript{II} phase of polymerized LLC membranes has
@@
 
+%MRS5: this is a better thesis. This sentence sets out a problem to the solved.
   Our current understanding of LLC systems is not rich enough to be able to
@@
   organic systems, we must first gain a thorough understanding of the nanoscopic
-  structure of LLC polymer membranes. Our approach to constructing a general
+  structure of LLC polymer membranes. 
+%MRS5: repeated use of model below, both constructing and developing?
+Our approach to constructing a general
   model will follow the development of a model of the assembly formed by
-  Na-GA3C11 since it has sufficient experimental characterization. We have also
+  Na-GA3C11 since it has sufficient experimental characterization. 
+%MRS5: maybe clean up/motivate abit more about why Col_h is worth starting with.
+We have also
   narrowed our scope to the development of a model of the Col\textsubscript{h}
@@
   Despite having structural data, there is still information which experiment
-  cannot definitively answer. Our current level of understanding suggests that
+  cannot definitively answer. 
+%MRS5: does a level of understanding suggest, or just is the level of understanding those facts?  and are there citations for these? are they inferred by the existing x-ray data.
+Our current level of understanding suggests that
   monomers partition into layers with head groups facing towards the center, then 
@@
 
-  While past work describes the Col\textsubscript{h} phase as dry
-  ~\cite{feng_scalable_2014}, it has been suggested by experimentalists, in
+  While past work describes the Col\textsubscript{h} phase as dry~\cite{feng_scalable_2014}, 
+  it has been suggested by experimentalists, in
   unpublished communications, that it is likely that neat monomer leaches small

### 2018-02-07 Ben_Manuscripts/structure_paper/Draft.tex
Updates to intro and supplemental

@@
   %properties in mind.  
-  The clearer picture of the nanoscopic structure of these membranes provided in this study will enable better understanding of the mechanisms of small molecule transport within these nanopores.
+  The clearer picture of the nanoscopic structure of these membranes provided
+  in this study will enable better understanding of the mechanisms of small
+  molecule transport within these nanopores.
 
@@
 %solving.
+
+  Problem to be solved
 
@@
 
-%MRS5: a more compelling thesis is that we need membranes that are more selective than RO and NF.  
-  RO and NF are finding applications beyond primarily water-based
-  purifications. Recovery of valued products from complex aqueous and organic
-  waste is of increasing interest. For example, flowback water (FW) produced
-  during hydraulic fracturing is a complex wastewater full of potentially
-  valuable dissolved organic compounds \cite{dischinger_application_2017}. There
-  is increasing pressure to reuse hydraulic fracturing water rather than dispose
-  of it in order to reduce social and envrionmental impacts as well as cost
-  \cite{theodori_hydraulic_2014}. Rather than dispose of the wastestream
-  generated in the recycling process, we can instead use highly selective
-  membranes in order to successfully recover the useful compounds.
+  We need membranes that are more selective than RO and NF. Recovery of valued
+  products from complex aqueous and organic waste is of increasing interest. For
+  example, flowback water (FW) produced during hydraulic fracturing is a complex
+  wastewater full of potentially valuable dissolved organic compounds
+  \cite{dischinger_application_2017}. There is increasing pressure to reuse
+  hydraulic fracturing water rather than dispose of it in order to reduce social
+  and envrionmental impacts as well as cost \cite{theodori_hydraulic_2014}.
+  Rather than dispose of the wastestream generated in the recycling process, we
+  can instead use highly selective membranes in order to successfully recover the
+  useful compounds.
 
@@
 
-%MRS5: maybe a more compelling thesis would be that LLC might have the capabilility to serve as selective membranes?
-  Lyotropic liquid crystals (LLCs) are amphiphilic molecules that have the
-  ability to self-assemble into porous nanostructures \cite{smith_ordered_1997}
-  which can be crosslinked to create mechanically strong membrane films with
-  pores on the order of 1 nm in diameter \cite{zhou_supported_2005}. Unlike
-  commercial NF membranes, LLC membrane pores are uniform in size. Since LLC
-  membranes lack a pore size distribution, they inherently exhibit high
-  selectivity due to their strict molecular weight cut-off (MWCO). 
-%MRS5: is there a citation for the strict MWCO? 
-%MRS5: suggested change.
- Additionally, the LLCs chosen to make membranes for this application are salts, and therefore lead to 
-Donnan exclusion of ions in solution.
- The membrane
-  gains a net surface charge when counterions from head groups that line the pore
-  walls escape into the feed solution in order to balance the gradients of
-  concentration and electric potential. 
-%This effect, which causes the membrane to
-%  repel incoming charged species, is called Donnan exclusion
-
-  \cite{donnan_theory_1995}.
+  Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
+  performing highly selective separations. LLCs are amphiphilic molecules that
+  have the ability to self-assemble into porous nanostructures
+  \cite{smith_ordered_1997} which can be crosslinked to create mechanically
+  strong membrane films with pores on the order of 1 nm in diameter
+  \cite{zhou_supported_2005}. Unlike commercial NF membranes, LLC membrane pores
+  are uniform in size. Since LLC membranes lack a pore size distribution, they
+  inherently exhibit high selectivity due to their strict molecular weight
+  cut-off (MWCO) ~\cite{zhou_supported_2005}. Additionally, the LLCs chosen to
+  make membranes for this application are salts, and therefore lead to Donnan
+  exclusion of ions in solution. The membrane gains a net surface charge when
+  counterions from head groups that line the pore walls escape into the feed
+  solution in order to balance the gradients of concentration and electric
+  potential \cite{donnan_theory_1995}.
 
@@
   NaCl, Q\textsubscript{I} phase membrane filtration experiments have shown
-%MRS5: for dashes between two numbers, use double -- for the correct length in the file. 
   selectivity 2--3 times higher than commercial RO and 6--12 times higher than
@@
   its geometry should give optimal transport performance compared to the
-  Q\textsubscript{I} phase. 
-%MRS5: citation on this above?
-  The H\textsubscript{II} phase forms at room
-  temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
-  packed, straight, hydrophilic pore columns\cite{smith_ordered_1997}. In the
-  absence of water, neat monomer will form the same hexagonal columnar structure
-  which, in literature, has been referred to as the Col\textsubscript{h}
-  thermotropic phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}).
-  These hexagonal columnar phases represent the ideal geometry for membrane
-  transport. 
+  Q\textsubscript{I} phase \cite{matyka_tortuosity-porosity_2008}. The
+  H\textsubscript{II} phase forms at room temperature in the presence of c.a.~10
+  wt\% water and consists of hexagonally packed, straight, hydrophilic pore
+  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
+  form the same hexagonal columnar structure which, in literature, has been
+  referred to as the Col\textsubscript{h} thermotropic
+  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}).  These
+  hexagonal columnar phases represent the ideal geometry for membrane transport.
+
 %MRS5: maybe less about Q_I since it's not in this paper?  The introduction should be an introduction to the paper.
-The most promising Q\textsubscript{I} phase for membrane
-  applications forms at 70\degree C when monomer is mixed with c.a.~20 wt\%
-  glycerol\cite{carter_glycerol-based_2012}. The Q\textsubscript{I} phase
-  consists of a network of three dimensionally interconnected pores (See
-  Figure~\ref{fig:bcc_phases}). This complex geometry effectively adds a degree
-  of tortuosity to the membrane which prevents optimal through-plane transport.
-  Despite the geometric differences between the Q\textsubscript{I} and
-  H\textsubscript{II} phase, the chemical environment within the pores is
-  expected to be similar, and either membrane should be highly selective.
+%  The most promising Q\textsubscript{I} phase for membrane
+%  applications forms at 70\degree C when monomer is mixed with c.a.~20 wt\%
+%  glycerol\cite{carter_glycerol-based_2012}. The Q\textsubscript{I} phase
+%  consists of a network of three dimensionally interconnected pores (See
+%  Figure~\ref{fig:bcc_phases}). This complex geometry effectively adds a degree
+%  of tortuosity to the membrane which prevents optimal through-plane transport.
+%  Despite the geometric differences between the Q\textsubscript{I} and
+%  H\textsubscript{II} phase, the chemical environment within the pores is
+%  expected to be similar, and either membrane should be highly selective.
 

### 2018-02-07 Ben_Manuscripts/structure_paper/supplemental.tex
Updates to intro and supplemental

@@
 	\fontsize{14pt}{12pt}\selectfont
-	\textbf{Experimental correlation length of R-$\pi$}
+	\textbf{\noindent Experimental correlation length of R-$\pi$}
   \endgroup
@@
   maximum (FWHM) is related to the correlation length, L, by the relationship: $
-  L = \frac{\pi}{FWHM} $. The error in the value is calculated as the square root
+  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
   of the diagonal entry of the covariance matrix calculated 
@@
   \end{figure}
-
+  \vspace{1em} \\
   %Our model is insensitive to initial configuration if monomer placement is chosen within reason. 
@@
 
-		\item 55 \AA~: We tested a pore spacing of 55 \AA~ which is at
+		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
 		a distance where monomers in each pore no longer intersect adjacent pores. Once
@@
 	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
-	  pore spacing constant at 45 \AA~ and the distance between layers constant at
-	  3.7 \AA. Equilibrated values of pore radii are presented in
-	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated as the
-	  average distance of all carbonyl carbons (See
+	  pore spacing constant at 45 \AA~and the initial distance between layers
+	  constant at 3.7 \AA. Equilibrated values of pore radii are presented in
+	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
+	  as the average distance of all carbonyl carbons (See
 	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
@@
 		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
-		agrees with the 2.5 \AA~ configuration within error.
+		agrees with the 2.5 \AA~configuration within error.
 
@@
 		full dry equilibration procedure, we see a combination of cylindrical and
-		slit-like pores (Figure~\ref{fig:slits}). We are wary of such a non-symmetric
-		structure and choose not to use a pore radius of 8 \AA for our starting configurations.
+		slit-like pores (Figure~\ref{fig:slits}). Measuring the pore radius of this
+		system does not have a concrete meaning since slits do not have a single
+		radius, but its calculated value is reported in Table ~\ref{table:radii}. We
+		are wary of such a non-symmetric structure and choose not to use a pore radius
+		of 8 \AA~for our starting configurations.
 
@@
 	  stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
-	  will focus the discussion here on systems built with layers stacked 10~\AA
+	  will focus the discussion here on systems built with layers stacked 10 \AA~
 	  apart.
@@
 
+  \vspace{1em}
   Crosslinking of the the monomer Na-GA3C11 occurs by a UV initiated free

### 2018-02-07 Ben_Manuscripts/structure_paper/Draft.tex
Updates to intro

@@
 
-%MRS5: want to get people engaged from the beginning. The first
-%paragraph should describe a problem to be solved. Then you can get
-%into the motivating details (like background of the alternatives, and
-%why we need something different).  I feel like this is an
-%introduction into different types of membranes, though it should be
-%an introduction to the problem that this paper takes steps towards
-%solving.
-
-  Problem to be solved
-
-  Reverse osmosis (RO) and nanofiltration (NF) are membrane-based separation
-  processes widely used to create potable or reusable water by removing salts and
-  other dissolved compounds from water sources. RO membranes are typically thin
-  film composite (TFC) membranes with a porous support layer and a dense
-  crosslinked polymer active layer which near indiscriminately 
-%MRS5: 
-%  Maybe ``impermeable to all solutes?'' or ``separates all solutes from water.''  As written, it's not stated what the solutes are separated from.
-  separates all solutes. 
-NF membranes have porous architectures with pores on the order of 1 nm
-  in size which separate primarily based on solute size
-  \cite{van_der_bruggen_review_2003}.
-
-  We need membranes that are more selective than RO and NF. Recovery of valued
-  products from complex aqueous and organic waste is of increasing interest. For
-  example, flowback water (FW) produced during hydraulic fracturing is a complex
+  %MRS5: want to get people engaged from the beginning. The first paragraph
+  %should describe a problem to be solved. Then you can get into the motivating
+  %details (like background of the alternatives, and why we need something
+  %different).  I feel like this is an introduction into different types of
+  %membranes, though it should be an introduction to the problem that this paper
+  %takes steps towards solving.
+
+  A highly selective membrane can be useful for the recovery of valuable products
+  from complex aqueous and organic waste.
+  %We need membranes that are more selective than RO and NF. Recovery of valued
+  %products from complex aqueous and organic waste is of increasing interest. 
+  For example, flowback water (FW) produced during hydraulic fracturing is a complex
   wastewater full of potentially valuable dissolved organic compounds
@@
   hydraulic fracturing water rather than dispose of it in order to reduce social
-  and envrionmental impacts as well as cost \cite{theodori_hydraulic_2014}.
+  and environmental impacts as well as cost \cite{theodori_hydraulic_2014}.
   Rather than dispose of the wastestream generated in the recycling process, we
-  can instead use highly selective membranes in order to successfully recover the
+  can instead use highly selective membranes in order to successfully recover
   useful compounds.
@@
   relative diffusivities of desired and undesired solutes.
+
+% BJC: Maybe I don't even need to dive into explaining RO and NF.
+%  Reverse osmosis (RO) and nanofiltration (NF) are membrane-based separation
+%  processes widely used to create potable or reusable water by removing salts and
+%  other dissolved compounds from water sources. RO membranes are typically thin
+%  film composite (TFC) membranes with a porous support layer and a dense
+%  crosslinked polymer active layer which  separates all solutes from water. NF
+%  membranes have porous architectures with pores on the order of 1 nm in size
+%  which separate primarily based on solute size
+%  \cite{van_der_bruggen_review_2003}.
 
@@
 
-  The feasiblity of LLC membranes has been demonstrated using LLCs that form
+  The feasibility of LLC membranes has been demonstrated using LLCs that form
   the type 1 bicontinuous cubic (Q\textsubscript{I})
@@
 
-%MRS5: be more explicit about current efforts. Also use the
-%opportunity of a thesis statement to convince the readership of
-%something.  what do you want to convince them?
-  We will focus our current efforts around the H\textsubscript{II} phase since
-  its geometry should give optimal transport performance compared to the
-  Q\textsubscript{I} phase \cite{matyka_tortuosity-porosity_2008}. The
-  H\textsubscript{II} phase forms at room temperature in the presence of c.a.~10
-  wt\% water and consists of hexagonally packed, straight, hydrophilic pore
-  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
-  form the same hexagonal columnar structure which, in literature, has been
-  referred to as the Col\textsubscript{h} thermotropic
-  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}).  These
-  hexagonal columnar phases represent the ideal geometry for membrane transport.
+  The H\textsubscript{II} phase pore geometry is better for transport than the
+  Q\textsubscript{I} phase. The H\textsubscript{II} phase forms at room
+  temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
+  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
+  water, neat monomer will form the same hexagonal columnar structure which, in
+  literature, has been referred to as the Col\textsubscript{h} thermotropic
+  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}).  The most
+  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
+  C when monomer is mixed with c.a.~20 wt\%
+  glycerol\cite{carter_glycerol-based_2012}. Q\textsubscript{I} phase membranes
+  consist of a tortuous network of three dimensionally interconnected pores that
+  prevent optimal through-plane transport. The densely packed, non-tortuous and
+  uniform sized pores of H\textsubscript{II} phase membranes represents the ideal
+  geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
+  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
+  liquid crystalline domains, formed during self-assembly of NA-GA3C11 monomers, are
+  isotropically aligned which is detrimental to membrane performance.
 
@@
 %MRS5: not a strong thesis.  Why has it been revived?  The reasons for that would be a better thesis.
-  Research into the H\textsubscript{II} phase of polymerized LLC membranes has
-  been revived in recent years. During early stages of exploration, hexagonal
-  mesophases formed by Na-GA3C11 (Figure~\ref{fig:assembly}) could not be
-  macroscopically aligned, resulting in low flux membranes, and no clear route
-  towards scalable and economical filtration. For this reason, research efforts
-  focused on the Q\textsubscript{I} phase, whose geometry does not require
-  alignment. In 2014, Feng et al.~showed that one can align 
-  Col\textsubscript{h} mesophases using a magnetic field with subsequent
-  cross-linking to lock the structure in place \cite{feng_scalable_2014}. In
-  2016, Feng et al. showed that one could obtain the same result using a second
-  technique termed soft confinement \cite{feng_thin_2016}. Current efforts are
-  focused on extending the method to the H\textsubscript{II} phase and 
-  characterizing the performance of these newly aligned systems.
+  Recently, researchers have learned how to macroscopically align the hexagonal
+  domains which has revived research into H\textsubscript{II} phase LLC membranes.
+%  Research into the H\textsubscript{II} phase of polymerized LLC membranes has
+%  been revived in recent years. 
+%  During early stages of exploration, hexagonal
+%  mesophases formed by Na-GA3C11 (Figure~\ref{fig:assembly}) could not be
+%  macroscopically aligned, resulting in low flux membranes, and no clear route
+%  towards scalable and economical filtration. 
+%  For this reason, research efforts
+  Previously, research efforts were focused on the Q\textsubscript{I} phase,
+  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
+  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
+  subsequent cross-linking to lock the structure in place
+  \cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
+  the same result using a second technique termed soft confinement
+  \cite{feng_thin_2016}. Current efforts are focused on extending the method to
+  the H\textsubscript{II} phase and characterizing the performance of these newly
+  aligned systems.
 
@@
 
-%MRS5: this is a better thesis. This sentence sets out a problem to the solved.
   Our current understanding of LLC systems is not rich enough to be able to
@@
 
-  %BJC: I think the first sentence of the following paragraph is
-  %necessary to put somewhere, but maybe not in this spot exactly
+  Here we develop a model of the Col\textsubscript{h} assembly formed by
+  Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
+  phase is a simpler starting point. The system has no water which will allow us
+  to simulate longer timescales, and there exists detailed experimental
+  characterization of the fully aligned state, including 2D wide-angle X-ray
+  scattering (WAXS) patterns which are useful for reconstructing structural data.
+  We anticipate using this Col\textsubscript{h} model in order to build an 
+  H\textsubscript{II} model in the future.
+  %The two phases appear to share similar structural characteristics since the
+  %pore spacings in each system are in close agreement
+  %\cite{feng_thin_2016,resel_structural_2000}.
+
   In order to appropriately model transport in these ordered, nanoporous
   organic systems, we must first gain a thorough understanding of the nanoscopic
-  structure of LLC polymer membranes. 
-%MRS5: repeated use of model below, both constructing and developing?
-Our approach to constructing a general
-  model will follow the development of a model of the assembly formed by
-  Na-GA3C11 since it has sufficient experimental characterization. 
-%MRS5: maybe clean up/motivate abit more about why Col_h is worth starting with.
-We have also
-  narrowed our scope to the development of a model of the Col\textsubscript{h}
-  phase membrane. Compared to the H\textsubscript{II} phase, the
-  Col\textsubscript{h} phase is a simpler starting point, due to the absence of
-  water, and has detailed experimental wide-angle X-ray scattering (WAXS)
-  patterns useful for reconstructing structural data. The two phases appear to
-  share similar structural characteristics since the pore spacings in each system
-  are in close agreement \cite{feng_thin_2016,resel_structural_2000}.
-
-  Despite having structural data, there is still information which experiment
-  cannot definitively answer. 
-%MRS5: does a level of understanding suggest, or just is the level of understanding those facts?  and are there citations for these? are they inferred by the existing x-ray data.
-Our current level of understanding suggests that
-  monomers partition into layers with head groups facing towards the center, then 
-  stack on top of each other to create pores that pack together hexagonally.
-  There are several key questions that we will investigate in order to
-  expand this understanding:
+  structure of LLC polymer membranes. Our current level of understanding about
+  the structure at the nanoscale is limited. Using X-ray diffraction and TEM data
+  we can infer that monomers aggregate into hexagonally packed columns with their
+  head groups facing towards the column center. There remain several key questions
+  that we will investigate in order to expand this understanding:
 

### 2018-02-21 Ben_Manuscripts/structure_paper/Draft.tex
Read through draft and fixed things

@@
   \begin{abstract}
-  %MRS5: Abstract can contain a little less introduction material. Suggest the following cuts  
+
   Nanostructured porous membranes made from the cross-linked hexagonal phase of
   self-assembled lyotropic liquid crystals (LLCs) are a promising material for
-  selective separations. 
-  %To date, their separation performance has only been
-  %characterized with membranes made from a small set of LLC monomers. There
-  %remains a large design space that we can likely exploit to design membranes for
-  %solute specific separations. 
-  In this work, we develop an atomistic molecular
-  model of an LLC membrane. We show that our model is maximally consistent with
+  selective separations.  In this work, we develop an atomistic molecular model
+  of an LLC membrane. We show that our model is maximally consistent with
   experimental observations by comparing simulated X-ray Diffraction (XRD)
@@
   We explore, in depth, the composition and structure of the nanopores in order
-  to give insights that are not easily accessible to experimentalists. 
-  %MRS5: suggest:
-  %With the
-  %clear picture of the nanoscopic structure of these membranes gained from this
-  %work, we will be able to use the model to understand the mechanisms of small
-  %charged and uncharged solute transport within the nanopores, and eventually we
-  %will be able to screen large sets of modified monomers with their separation
-  %properties in mind.  
-  The clearer picture of the nanoscopic structure of these membranes provided
-  in this study will enable better understanding of the mechanisms of small
-  molecule transport within these nanopores.
+  to give insights that are not easily accessible to experimentalists.  The
+  clearer picture of the nanoscopic structure of these membranes provided in this
+  study will enable a better understanding of the mechanisms of small molecule
+  transport within these nanopores.
 
@@
 
-  A highly selective membrane can be useful for the recovery of valuable products
-  from complex aqueous and organic waste.
-  %We need membranes that are more selective than RO and NF. Recovery of valued
-  %products from complex aqueous and organic waste is of increasing interest. 
-  For example, flowback water (FW) produced during hydraulic fracturing is a complex
-  wastewater full of potentially valuable dissolved organic compounds
+  A highly selective membrane can be useful for the recovery of valuable
+  products from complex aqueous and organic solutions.  For example, flowback
+  water (FW) produced during hydraulic fracturing is a complex wastewater full of
+  potentially valuable dissolved organic compounds such as acetate
   \cite{dischinger_application_2017}. There is increasing pressure to reuse
@@
   and environmental impacts as well as cost \cite{theodori_hydraulic_2014}.
-  Rather than dispose of the wastestream generated in the recycling process, we
-  can instead use highly selective membranes in order to successfully recover
-  useful compounds.
+  Rather fully than dispose of the wastestream generated in the recycling
+  process, we can instead use highly selective membranes in order to successfully
+  recover useful compounds.
 
@@
 %MRS5: under solution-diffusion, then the free energy to partition into the membrane is important as well, correct?
-  Selective separation by a semipermeable membrane barrier is governed by two
+%BJC: but wouldn't the free energy just be a function of all the factors I list? 
+%Maybe I can rephrase it that way: "A solutes ability to enter a given membrane barrier is governed by the free energy to partition into the membrane which is influenced by ..."
+  Selective separation by a semipermeable membrane barrier can be broken into two
   steps: barrier entry and transport through the barrier. A solute's ability to
+  % BJC: can also come up with a third step: exit. Which I think is mostly chemical potential gradient
   enter a given membrane barrier is decided by its size, shape, charge, polarity
@@
 
+  % BJC: I like this figure, but I don't know if it is necessary in the main body. i  % Maybe move to supplemental. Thoughts?
   \begin{figure}
@@
 %MRS5: not sure Q should be in here.
-  \caption{The choice of LLC monomer leads to different favorable liquid
+  \caption{The choice of LLC monomer and solvent leads to different accessible liquid
         crystalline phases. The monomer shown in (a) forms the Q\textsubscript{I} phase
         in either the Ia3d (left) or Pn3m (right) space group. The surfaces shown
-        represent the interface between the hydrophilic and hydrophobic regions of unit
+        represent the interface between the hydrophilic and hydrophobic regions of the unit
         cell. As pictured, we assume that each region occupies an equal volume. The
@@
         (H\textsubscript{II} in the presence of water or Col\textsubscript{h} when no
-         water is present).}\label{fig:bcc_v_hII}
+         water is present) The blue region represent the hydrophilic pores while the cyan region represents the surrounding hydrophobic monomer tails.}\label{fig:bcc_v_hII}
   \end{figure}
@@
 
-  Our current understanding of LLC systems is not rich enough to be able to
-  precisely design membranes for specific separations. Over the past 20 years,
+  Our current understanding of LLC membrane systems is not rich enough to be
+  able to precisely design them for specific separations. Over the past 20 years,
   H\textsubscript{II}-phase LLC polymer membrane studies have been limited
@@
   the chemical environment in the nanopores of this or related materials for
-  small molecule separations. The only source of predictive modeling for
-  LLC systems have been macroscopic models that likely do not adequately describe
+  small molecule separations. The only source of predictive modeling for LLC
+  systems have been macroscopic models that likely do not adequately describe
   transport at these length scales \cite{hatakeyama_water_2011}. It will be
@@
   A molecular-level understanding of LLC polymer membrane structure, enabled by
-  molecular dynamics simulations, can provide guidelines to reduce the large
+  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
   chemical space available to design monomers for creation of separation-specific
@@
   counterions which may influence both the pore size and the strength of the
-  Donnan potential which affects the degree to which the membrane can exclude
-  charged species at the membrane surface.
+  Donnan potential
+
+  %which affects the degree to which the membrane can exclude
+  %charged species at the membrane surface.
 
@@
   there are 4 monomers in each layer \cite{zhu_methacrylated_2006}. Their model
-  likely does not sufficiently model the chemical environment present in the real
-  system since it only contains 16 total monomers. A separate calculation based
-  on the estimated volume of the liquid crystal monomers proposes that each layer
-  consists of seven monomers\cite{resel_structural_2000}. Our best chance to
-  answer this question is by using a molecular model orders of magnitude larger
-  than any other reported atomistic liquid crystal membrane simulation, as we
-  present here. We will directly change the layer composition and note its effect
-  on membrane structure.
+  likely does not sufficiently imitate the chemical environment present in the
+  real system since it only contains 16 total monomers. A separate calculation
+  for NA-GA3C11, based on the estimated volume of the liquid crystal monomers,
+  proposes that each layer consists of seven
+  monomers\cite{resel_structural_2000}. Our best chance to answer this question
+  is by using a molecular model orders of magnitude larger than any other
+  reported atomistic liquid crystal membrane simulation, as we present here. We
+  will directly change the layer composition and note its effect on membrane
+  structure.
+
+  \item How do monomers in each layer position themselves with respect to
+  surrounding layers? \label{point:orientation}
+
+  $\pi$-$\pi$ stacking interactions between aromatic monomer head groups may be
+  a driving force of self-assembly in this system \cite{gazit_possible_2002}. Gas
+  phase \textit{ab initio} studies of benzene dimers have shown a clear energetic
+  advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking
+  conformations over a sandwiched conformation \cite{sinnokrot_estimates_2002}.
+  Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking
+  attraction which favors the parallel displaced configuration in all cases
+  except where the substitutions are extremely electron
+  withdrawing\cite{waller_hybrid_2006,ringer_effect_2006}. In this study, we
+  compare simulated X-ray diffraction patterns to experiment in order to deduce
+  which stacking configuration is most likely. We also dive deeper into the
+  origin of features present in the 2D diffraction patterns.
 
@@
 
+  %BJC: Reordered, so changing the wording here.
   Indications of strong $\pi$-$\pi$ stacking interactions in the direction
-  perpendicular to the membrane plane support the existence of layers
-  experimentally. $\pi$-$\pi$ stacking will only occur between the aromatic
+  perpendicular to the membrane plane, combined with the wedge-like character of
+  the LLC monomers, suggests that monomers should arrange into disks that stack in
+  layers. $\pi$-$\pi$ stacking will only occur between the aromatic
   monomer head groups which leaves no description of what is happening in the
@@
   stacking order among headgroups.
-
-  \item How do monomers in each layer position themselves with respect to
-  surrounding layers? \label{point:orientation}
-
-  The $\pi$-$\pi$ stacking interactions may be a driving force of self-assembly
-  in this system \cite{gazit_possible_2002}. Gas phase \textit{ab initio} studies
-  of benzene dimers have shown a clear energetic advantage for parallel displaced
-  and T-shaped $\pi$-$\pi$ stacking conformations over a sandwiched conformation
-  \cite{sinnokrot_estimates_2002}. Substituted benzene rings exhibit an even
-  stronger $\pi$-$\pi$ stacking attraction which favors the parallel displaced
-  configuration in all cases except where the substitutions are extremely
-  electron withdrawing\cite{waller_hybrid_2006,ringer_effect_2006}. In this
-  study, we compare simulated X-ray diffraction patterns to experiment in order
-  to deduce which stacking configuration is most likely.
 
@@
   hexagonally packed, hydrophilic regions where transport is likely to occur.
-  One may instinctively assume that these regions are tube-like pathways. We will
-  explore the composition of the pores and the partition between the
+  One may instinctively assume that these regions are hollow tube-like pathways.
+  We will explore the composition of the pores and the partition between the
   hydrophilic and hydrophobic regions.
@@
 	respective quadrants. In many liquid crystal systems one can explain the spots
-	by the tilt angle of the alkane chains with respect to the membrane 
+	as the tilt angle of the alkane chains with respect to the membrane
 	plane\cite{govind_simple_2001}.
@@
   pore's central axis, does not influence the equilibrium structure if one choses
-  a reasonable value (See Supplemental Information). The pore radius is chosen to
-  be 0.5 nm in our initial configurations. The initial distance between pores
-  also has little effect on the the equilibrated structure (See Supplemental
-  Information). However, one should not start them too close or there will be
-  high energy repulsions during early equilibration. We chose an initial pore
-  spacing of 4.5 nm, $\sim$10\% larger than the experimental value of 4.12 nm.
-  The distance between layers, the rotation of the layers with respect to
-  adjacent layers, and the number of monomers per layer do influence the
-  equilibrium structure and require further justification for their choices. We
-  rely on experimental data to inform them.
+  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
+  configurations. The initial distance between pores also has little effect on
+  the the equilibrated structure However, one should not start them too close or
+  there will be high energy repulsions during early equilibration. We chose an
+  initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
+  of 4.12 nm.  A sensitivity analysis of both parameters is presented in
+  the supplemental information.  The distance between layers, the rotation of the
+  layers with respect to adjacent layers, and the number of monomers per layer do
+  influence the equilibrium structure and require further justification for their
+  choices. We rely on experimental data to inform them.
 
@@
   then allowed the system to readjust during equilibration. Each monomer was
-  rotated so the plane of the aromatic head groups would be coplanar with the xy
+  rotated so the plane of its aromatic head groups would be coplanar with the xy
   plane. We explored three different initial layer spacings. The first is exactly
@@
   \cite{sinnokrot_estimates_2002}. We ruled out the T-shaped configuration
-  because its $\sim$5 \AA~ equilibrium stacking distance
+  because its $\sim$5 \AA~equilibrium stacking distance
   \cite{sinnokrot_estimates_2002} is inconsistent with R-$\pi$. It is also
@@
 
-  The number of monomers in each layer is unknown, as stated in
+  The number of monomers in each layer is unknown, as stated in question
   (\ref{point:monomernum}). We tested configurations constructed with a varied
@@
   in all possible locations where an addition could occur. We carry out the
-  cross-linking procedure iteratively. During each iteration, the algoritm
+  cross-linking procedure iteratively. During each iteration, the algorithm
   selects eligible bonding carbon atoms based on a distance cut-off. The topology
@@
   Equation~\ref{eqn:nematic_order_parameter} to accomplish this by defining
-  $\mathbf{n}$ as the z-axis, or pore axis, and then measuring the angles,
+  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
   $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
@@
   a discrete Fourier transform to $g(z)$ and extracted the highest intensity
-  frequency.
+  frequency. We performed the same procedure to calculate $g(z)$ of the tails 
+  except instead of using the center of masses of the tails, we averaged $g(z)$
+  for each atom that makes up the tail.
 
   In two dimensions, we observed xy and xz pair distribution functions based on
-  the center of masses of the aromatic head group rings. We gave special
-  consideration to the xy cross-sections since multiple rings exist in the same
-  plane located at different vertices of a polygon. We used a rotated frame of
-  reference to avoid ambiguity in the final pair distribution functions. For a
-  given center of mass, we rotated the coordinates so that the vector created
-  from the center of mass to the pore center was in line with the positive
-  x-axis.
+  the center of masses of the aromatic head group rings. For the xy pair
+  distribution functions, we used a rotated frame of reference. For a given center
+  of mass, we rotated the coordinates so that the vector created from the center
+  of mass to the pore center was aligned with the positive x-axis.
+
+  %We gave special
+  %consideration to the xy cross-sections since multiple rings exist in the same
+  %plane located at different vertices of a polygon. We used a rotated frame of
+  %reference to avoid ambiguity in the final pair distribution functions. i
 
@@
   dependence on initial configuration. We calculated the average intensity within
-  R-alkanes of the experimental pattern, $I_{avg}$. We exclude intensities
-  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$ , since the simulated patterns differ
-  from experiment in those regions. Specifically, in contrast to the
-  experimental WAXS pattern, R-$\pi$ appearing in simulated diffraction patterns
-  intersects with R-alkanes (See Fig. \ref{fig:XRDsim}). We multiplied $I_{avg}$
-  by a scaling factor of 2.5. Intensities that appear in the experimental pattern
-  $\geq$ 2.5$I_{avg}$ receive colorbar values of 1. We apply the same scaling
-  method to the simulated patterns. We carefully chose a scaling factor of 2.5 in
-  order to (1) visibly display all features in the experimental pattern and (2)
-  to allow us to compare the relative intensities of features between simulated
-  and experimental diffraction patterns.
+  R-alkanes of the experimental pattern, $I_{avg}$. We exclude intensities within
+  $\pm$ 30\degree~of the meridional axis defined by $q_r=0$ , since the simulated
+  patterns differ from experiment in those regions in all cases. Specifically, in
+  contrast to the experimental WAXS pattern, R-$\pi$ appearing in simulated
+  diffraction patterns intersects with R-alkanes (See Fig. \ref{fig:XRDsim}). We
+  multiplied $I_{avg}$ by a scaling factor, $f$. Intensities that appear in the
+  experimental pattern $\geq$ $f\times I_{avg}$ are colored uniformly. We apply
+  the same scaling method to the simulated patterns. We carefully chose a scaling
+  factor of $f=3.1$ in order to (1) visibly display all features in the
+  experimental pattern and (2) to allow us to compare the relative intensities of
+  features between simulated and experimental diffraction patterns.
 
@@
   \subsection{Structural Characterization}
+
   \subsubsection{Number of monomer per layer}
@@
   Question (\ref{point:metastable}), however not all will make physical sense or fit
-  the experimental profile that we are looking to match. Figure~\ref{fig:p2p}
+  the experimental profile that we are trying to match. Figure~\ref{fig:p2p}
   shows the pore spacing for all systems tested. Systems built with 5 monomers in
@@
 	\includegraphics[width=\linewidth]{p2p.png}
-	\caption{When we build systems with 5 monomers per layer in the
-		parallel displaced configuration, the equilibrated pore spacing is closest to
-		the experimental value of 4.12 nm. The equilibrated pore spacing of the model
-		increases as the number of monomers in each layer increases. The pore spacing
-		of systems starting in the sandwiched configuration is systematically 
-		lower than those started in the parallel displaced configuration.}~\label{fig:p2p}
+	\caption{When we build systems with 5 monomers per layer , the
+		equilibrated pore spacing is closest to the experimental value of 4.12 nm. The
+			equilibrated pore spacing of the model increases as the number of monomers in
+			each layer increases. The pore spacing of systems starting in the sandwiched
+			configuration is systematically lower than those started in the parallel
+			displaced configuration.}~\label{fig:p2p}
   \end{figure}
@@
   R-$\pi$ since the nearest vertically stacked head group to any given head group
-  is 7.4 \AA~away.
+  is $2\times$R-$\pi$~away.
 
@@
 	  present in the experimental WAXS pattern (b). The simulated XRD pattern
-	  generated from the equilibrated trajectory in the sandwiched configuration shows
+	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
 	  all major reflections except R-helix.}
@@
   % now I am having a hard time finding it again. 
-  The system we have modeled has bulky tails whose entropic contributions compete
+  The monomers in our model have bulky tails whose entropic contributions compete
   with the $\pi$-$\pi$ stacking interaction energy. There have been efforts to
@@
 
-  The R-spots signal, which appears in both simulated XRD patterns, is a result
-  of hexagonal alkane chain packing. Previous literature has explained the spots
-  in the diffraction pattern as the product of tilted alkane chains. We measured
-  the tilt angle of the alkane chains and showed that our system equilibrates to
-  an average tilt angle close to zero degrees (Fig.~\ref{fig:tilt}). To
-  understand the origin of the spots, we determined which atoms gave rise to the
-  feature. Since R-spots is present as higher intensity spots within R-alkanes,
-  it is likely that the spots arise as a consequence of the tails. By removing
-  all non-tail atoms from the trajectory and simulating a diffraction pattern, we
-  were able to isolate the cause of the spots to the tails
-  (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted the
-  centroids of the tails and measured the angle between each centroid and its
-  nearest neighbors with respect to the plane of the membrane. We see distinct
-  peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).
+  The R-spots signal, which appears in both simulated XRD patterns, is not a
+  result of alkane chain tilt. Previous literature has attributed the spots in
+  this particular WAXS pattern as the product of tilted alkane
+  chains~\cite{feng_scalable_2014}. We measured the tilt angle of the alkane
+  chains and showed that our system equilibrates to an average tilt angle close
+  to zero degrees (Fig.~\ref{fig:tilt}). To understand the origin of R-spots,
+  we determined which atoms gave rise to the feature. Since R-spots is present as
+  higher intensity spots within R-alkanes, it is likely that the spots arise as a
+  consequence of the tails. By removing all non-tail atoms from the trajectory
+  and simulating a diffraction pattern, we were able to isolate the cause of the
+  spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat,
+  we plotted the centroids of the tails and measured the angle between each
+  centroid and its nearest neighbors with respect to the plane of the membrane.
+  We see distinct peaks in the distribution of these angles
+  (Figure~\ref{fig:tail_packing}).
 
@@
   is a reconcilable difference with our simulated results.
+
+  The evidence supports the hypothesis that alkane chain tails pack in a
+  hexagonal array. Groups of three tails associated with each monomer prefer to
+  sit between tails of vertically stacked monomers rather than stacking directly
+  on top of them (Figure blah blah blah). This type of packing has been seen
+  before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.
 
@@
   pores indicated by the non uniformity in $g(y,z)$ in adjacent columns (along $y
-  = \pm 3.65$).Parallel displaced layers display weaker correlations but do not
+  = \pm 3.65$). Parallel displaced layers display weaker correlations but do not
   decay in their intensity as z increases. We do not see correlation between
@@
   will be grouped into the disordered pore basin, while those built with layers
-  initially stacked 3.7 \AA~apart will be grouped into the ordered basin.
+  initially stacked 3.7 \AA~apart will be grouped into the ordered pore basin.
 
@@
   with neighboring layers up to more than 10 layers away. This behavior deviates
-  from experimental evidence. The experimental correlation length suggests that
-  layers are correlated with about 3 neighboring layers which is closer to the
-  values exhibited by the disordered pore basin. We may need to simulate a system
-  with many more layers in order to reduce the correlation contributed by
-  periodic copies of the system.
-
-% BJC: below is summarized in methods
-%  We expect that the head groups in more ordered systems will be predominantly
-%  coplanar with the xy plane. We defined a director vector, \textbf{n}, as the
-%  vector normal to the plane of the monomer's aromatic head group, then measured
-%  the distribution of angles between it and the z-axis. We used the resulting
-%  distibution of angles to calculate the nematic order parameter, S. 
+  from experimental evidence. The experimental correlation length (See
+  supplemental information for details its derivation) suggests that layers are
+  correlated with about 3 neighboring layers which is closer to the values
+  exhibited by the disordered pore basin. We may need to simulate a system with
+  many more layers in order to reduce the correlation contributed by periodic
+  copies of the system.
+
   We calculated the nematic order parameter for each system using Equation
@@
   supplemental material. In general, ordered pore basin systems are more
-  nematically ordered than disordered pore basin systems. The head groups of the
-  disordered pore basin have more rotational freedom about the xy plane likely
-  due to the larger separation between layers.
+  nematically ordered than disordered pore basin systems and sandwiched
+  configuration systems are more nematically ordered than parallel displaced
+  configuration systems. The head groups of the disordered pore basin have more
+  rotational freedom about the xy plane likely due to the larger separation
+  between layers. Similarly, monomers situated in the sandwiched configuration
+  are constrained by other monomers stacked directly above and below them, while
+  monomers in the parallel displaced configuration have no direct neighbors
+  vertically which provides them with more rotational freedom.
 
@@
   the ordered pore basin. Correlation lengths in the disordered pore basin are
-  in closer agreement with experiment.}~\label{table:nematic}
+  in closer agreement with experiment. WHY IS THIS BOLD??!}~\label{table:nematic}
   \end{table}
@@
 
+  %BJC: this might be better situated before the numerical calculations that go 
+  %into Table 1
   We observe evidence of disorder in the xy plane of the disordered pore basin when
@@
                 \centering
-                \includegraphics[width=\linewidth]{offset_xy_correlation.png}
-                \caption{Parallel Displaced, Ordered Pore Basin}~\label{fig:offset_xy}
-        \end{subfigure}
-        \begin{subfigure}{0.47\linewidth}
-                \centering
                 \includegraphics[width=\linewidth]{disorder_xy_correlation.png}
@@
                 \centering
+                \includegraphics[width=\linewidth]{offset_xy_correlation.png}
+                \caption{Parallel Displaced, Ordered Pore Basin}~\label{fig:offset_xy}
+        \end{subfigure}
+        \begin{subfigure}{0.47\linewidth}
+                \centering
                 \includegraphics[width=\linewidth]{disorder_offset_xy_correlation.png}
@@
   \caption{$g(x,y)$ for sandwiched and parallel displaced configurations in the
-	  ordered and disordered pore basins illustrate disorder present in the xy plane
-	  when initial configuration layers are stacked 5\AA
-	  apart.}\label{fig:xy_correlation}
-  \end{figure}
+	  ordered and disordered pore basins illustrates the increase in xy plane
+	  disorder when initial configuration layer stacking distance is increase from
+	  3.7\AA~ to 5\AA~apart.}\label{fig:xy_correlation}
+  \end{figure}
+
+  \subsection{Slow dynamics}
+
+  %BJC: Matt thinks this section is necessary
+
+  We observe unusually slow dynamics in our system. Typical diffusion constants
+  for columnar liquid crystals have been reported to be on the order of
+  $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
+  constants of monomers in each of the systems we studied (Table~\ref{table:msd})
+  and learned that they are all on the order of $10^{-14}~m^2/s$. Our systems may
+  be frozen in a glassy state. It is also possible that we are simply observing
+  characteristics of the experimental system. There has been no experimental work
+  done to study diffusion of NA-GA3C11 monomers in the Col\textsubscript{h}
+  system and no measurement of the glass transition temperature. Such a low
+  diffusion constant is not unheard of. A more recent study reported a diffusion
+  constant of $1.2\times10^{-14}~m^2/s$ for a different liquid crystal that
+  formed a hexagonal columnar phase \cite{dvinskikh_molecular_2002}.
+
+  It is possible that our equilibration procedure may induce glassy phase
+  configurations. We have already shown that our system has some dependence on
+  initial configuration. It is conceivable that after a fast initial relaxation,
+  the system gets locked into a structure close to its initial configuration.
+  The glassy state of these systems may be the reason we observe such high
+  correlation lengths in the ordered pore basin systems.  Unfortunately, we are
+  unable to resolve the exact atomistic structure using existing experimental
+  techniques, so we are left to find out which initial configuration results in a
+  model with the closest match to experimental data.
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cc}
+  \toprule
+  System & Diffusion Constant ($m^2/s$) \\ 
+  \midrule
+  Sandwiched, Ordered & $10^{-14}$ \\
+  Parallel Displaced, Ordered & $10^{-14}$ \\
+  Sandwiched, Disordered & $10^{-14}$ \\
+  Parallel Displaced, Disordered & $10^{-14}$ \\
+  \bottomrule
+  \end{tabular}
+  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
+  which is three orders of magnitude lower than literature values.}~\label{table:msd}
+  \end{table}
 
@@
 
-  In order to address (\ref{point:poredefinition}), we plotted the number
-  densities of heavy atoms in the head group, carbon atoms in the tail region
-  and the sodium ions (Figure~\ref{fig:densities}). For the head group region,
-  we used the carbon atoms making up the aromatic ring. For the tail region we
-  used only carbon atoms of the monomer tails (See Supplemental Information for
-  diagram). We average the histograms over at least 50 ns of equilibrated trajectory.
+  In order to address Question (\ref{point:poredefinition}), we plotted the
+  number densities of heavy atoms in the head group, carbon atoms in the tail
+  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
+  region, we used the carbon atoms making up the aromatic ring. For the tail
+  region we used only carbon atoms of the monomer tails (See Supplemental
+  Information for diagram). We average the histograms over at least 50 ns of
+  equilibrated trajectory.
 
@@
   maximum. This implies a more uniform distribution of head groups within the
-  pore center. 
+  pore center. This is the same conclusion drawn from the plots of $g(x,y)$ 
+  (Figure~\ref{fig:xy_correlation}). 
   % High vacancy is less likely to be stable in the real system
@@
 
-  We explored the affect of water on pore structure, addressing (\ref{point:water})
-%  We answered (\ref{point:water}) and further support (\ref{point:orientation})
-  by preparing parallel displaced and sandwiched configurations according to the
-  wet equilibration procedure. There is no experimental measurement of trace
-  water concentration in the pores so we tested a range of water concentrations
-  from 0.5 to 5 percent. Our lower bound models a system with on average 2 water
-  molecules for each monomer layer. Figure~\ref{fig:solvation} shows the
-  simulated diffraction patterns resulting from each configuration.
+  We explored the affect of water on pore structure, addressing Question
+  (\ref{point:water}), by preparing parallel displaced and sandwiched
+  configurations according to the wet equilibration procedure. There is no
+  experimental measurement of trace water concentration in the pores so we tested
+  a range of water concentrations from 1 to 5 percent. Our lower bound models a
+  system with on average 2 water molecules for each monomer layer.
+  % BJC: double check this^ calculation or omit
+  Figure~\ref{fig:solvation} shows the simulated diffraction patterns resulting
+  from each configuration.
 
@@
   observe the existence of ions, head groups and water outside the pore region,
-  however in the hydrated system, the head groups drift beyond 1.5 \AA~from the
-  pore center. In the dry systems, head groups did not wander beyond 1.4 \AA~from
+  however in the hydrated system, the head groups drift beyond 1.5 nm from the
+  pore center. In the dry systems, head groups did not wander beyond 1.4 nm from
   the pore center. Both observations suggest that water pushes all components
   radially outward from the pore center, characteristic of a swelling process.
-  This system is a closer representation of the H\textsubscript{II} phase which
-  is typically synthesized with ca. 8 wt\% water. Further investigation of
-  hydrated systems can help unravel the mechanisms for selective transport in
-  separations of aqueous solutions.
+  The plots of $g(x,y)$ for dry and wet systems are compared in
+  Figure~\ref{fig:solvated_correlation}. They further illustrate how the system
+  swells in the presence of water. This system is a closer representation
+  of the H\textsubscript{II} phase which is typically synthesized with ca. 8 wt\%
+  water. Further investigation of hydrated systems can help unravel the
+  mechanisms for selective transport in separations of aqueous solutions.
 
@@
   \caption{Water fills the membrane pores in the parallel displaced (a) and
-	  sandwiched (b) configurations. We define the pore region to be within 0.6 nm of
-	  the pore center. Head groups in the sandwiched configuration sit closer to the
-	  pore center than they do in the parallel displaced configuration. The parallel
-	  displaced pores are composed primarily of water close to the pore center.}
+	  sandwiched (b) configurations. Head groups in the sandwiched configuration sit
+	  closer to the pore center than they do in the parallel displaced configuration.
+	  Both systems are composed primarily of water close to the pore center.}
   \label{fig:water_density}
   \end{figure}
-  %MRS4: weird there's a head group peak in the center. Not enough statistics, so shot noise from the r^2 dr weighting?
-  %BJC3: Yea, I'm not sure exactly. I'll look more into it. It might one or two head groups that just get stuck there.
-  % The pore I picture in the supplemental info is completely cleared of any head groups.
-
+
+  %BJC: this may be okay to push to supplemental
   \begin{figure}
@@
         \includegraphics[width=1\linewidth]{layered_xy_correlation.png}
-        \caption{Parallel Displaced, Ordered Pore Basin}
+        \caption{Sandwiched, Dry}
         \label{fig:layered_xy_correlation_comparison}
@@
         \includegraphics[width=1\linewidth]{layered_solvated_xy_correlation.png}
-        \caption{Sandwiched, Ordered Pore Basin}
+        \caption{Sandwiched, Solvated}
         \label{fig:layered_solvated_xy_correlation}
@@
         \includegraphics[width=1\linewidth]{offset_xy_correlation.png}
-        \caption{Parallel Displaced, Disorderd Pore Basin}
+        \caption{Parallel Displaced, Dry}
         \label{fig:offset_xy_correlation_comparison}
@@
         \includegraphics[width=1\linewidth]{offset_solvated_xy_correlation.png}
-        \caption{Sandwiched, Disordered Pore Basin}
+        \caption{Sandwiched, Solvated}
         \label{fig:offset_solvated_xy_correlation}
   \end{subfigure}
-  \caption{}~\label{fig:solvated_correlation}
+  \caption{$g(x,y)$ of monomer head groups illustrates how the pores
+	  swell in the presence of water.}~\label{fig:solvated_correlation}
   \end{figure}
@@
 
-  We used the equilibrated ordered parallel displaced system to calculate ionic
-  conductivity since its structure is the closest match to experiment. The model
-  gives reasonable estimates of ionic conductivity when compared to experiment.
-  We compare calculated values of ionic conductivity obtained using the
-  Nernst-Einstein relation and Collective Diffusion model in
+  We used the equilibrated parallel displaced system in the ordered pore basin
+  to calculate ionic conductivity since its structure is the closest match to
+  experiment. The model gives reasonable estimates of ionic conductivity when
+  compared to experiment.  We compare calculated values of ionic conductivity
+  obtained using the Nernst-Einstein relation and Collective Diffusion model in
   Figure~\ref{fig:conductivity}. The two methods agree with each other within
@@
   been shown that there is a large dependence of ionic conductivity on the
-  alignment of the pores. The ionic conductivity of an unaligned film is ca. 85
-  times lower than that of a nearly aligned film referenced here. We hypothesize
-  that a thin, perfectly aligned film would have a value of ionic conductivity in
-  closer agreement with our model.
+  alignment of the pores. The ionic conductivity of an isotropically aligned film
+  is ca. 85 times lower than that of a nearly aligned film referenced
+  here~\cite{feng_scalable_2014}. We hypothesize that a thin, perfectly aligned
+  film would have a value of ionic conductivity in closer agreement with our
+  model.
 
@@
   significantly when we applied the cross-linking algorithm to the equilibrated
-  parallel-displaced configuration built with 5 monomers per layer. We simulated
+  parallel-displaced configuration in the ordered pore basin. We simulated
   the cross-linked system in the NPT ensemble for 100 ns. After the system is
@@
   stack to create pores and that each layer contains 5 monomers. We see periodic
-  spacing of layers based on the z-direction correlation function, $g(z)$ of
+  spacing of layers based on the z-direction correlation function, $g(z)$, of
   atoms in the tails and separately of atoms in the head groups. Systems not
@@
   the membrane becomes thicker.
+
+  We acknowledge that our simulated system exhibits glassy dynamics. The
+  measured diffusion constants of monomers are three orders of magnitude lower
+  than expected. It is possible that our equilibration procedure induces these
+  types of metastable phases. It is also possible that the observed dynamics are
+  characteristic of the real system. We took great care to overcome the potential
+  limitations of our equilibration procedure and have come up with a structure
+  that is in good agreement with experimental data.
 

### 2018-02-23 Ben_Manuscripts/structure_paper/Draft.tex
New figures, updated figures, text edits on draft and supplemental

@@
 
-  A highly selective membrane can be useful for the recovery of valuable
+  A highly selective membrane would be useful for the recovery of valuable
   products from complex aqueous and organic solutions.  For example, flowback
@@
 %MRS5: under solution-diffusion, then the free energy to partition into the membrane is important as well, correct?
-%BJC: but wouldn't the free energy just be a function of all the factors I list? 
-%Maybe I can rephrase it that way: "A solutes ability to enter a given membrane barrier is governed by the free energy to partition into the membrane which is influenced by ..."
-  Selective separation by a semipermeable membrane barrier can be broken into two
-  steps: barrier entry and transport through the barrier. A solute's ability to
+%  Selective separation by a semipermeable membrane barrier can be broken into two
+%  steps: barrier entry and transport through the barrier. A solute's ability to
   % BJC: can also come up with a third step: exit. Which I think is mostly chemical potential gradient
-  enter a given membrane barrier is decided by its size, shape, charge, polarity
-  and how those factors combine to interact with the membrane material. The same
-  properties affect the rate at which a solute travels across the barrier. Since
-  undesired solutes may still enter the membrane, their diffusion rates relative
-  to desired solutes are important
-  \cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}. To achieve optimum
-  selectivity, it is necessary to design membranes in a way that one can tune the
-  relative diffusivities of desired and undesired solutes.
+%  enter a given membrane barrier is decided by its size, shape, charge, polarity
+%  and how those factors combine to interact with the membrane material. The same
+%  properties affect the rate at which a solute travels across the barrier. Since
+%  undesired solutes may still enter the membrane, their diffusion rates relative
+%  to desired solutes are important
+%  \cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}. To achieve optimum
+%  selectivity, it is necessary to design membranes in a way that one can tune the
+%  relative diffusivities of desired and undesired solutes.
+
+  Selective separation by a semipermeable membrane barrier is a function of the
+  geometric and chemical interactions of solutes with the membrane material. A
+  molecule's size, shape, charge and polarity combine to determine the degree to
+  which a solute partitions into a membrane and how fast it travels through the
+  membrane. To separate a component from a mixture, one must understand how to
+  design membranes in order to tune the relative transport rates of desired and
+  undesired solutes\cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}.
 
@@
   inherently exhibit high selectivity due to their strict molecular weight
-  cut-off (MWCO) ~\cite{zhou_supported_2005}. Additionally, the LLCs chosen to
-  make membranes for this application are salts, and therefore lead to Donnan
-  exclusion of ions in solution. The membrane gains a net surface charge when
-  counterions from head groups that line the pore walls escape into the feed
+  cut-off (MWCO) ~\cite{zhou_supported_2005}. Additionally, the LLC monomers
+  chosen to make membranes for this application are salts, and therefore lead to
+  Donnan exclusion of ions in solution. The membrane gains a net surface charge
+  when counterions from head groups that line the pore walls escape into the feed
   solution in order to balance the gradients of concentration and electric
@@
   from the pore centers, then normalized by the volume of the annulus defined by
-  the bin edges and the z box vector.
+  the bin edges and the z box vector (See supplemental information for a 
+  diagram).
 
@@
   measured ion concentration with respect to the volume of the entire unit cell. 
-
   The second method, termed the Collective Diffusion model, measures the
@@
   the measured equilibrated pore-to-pore distances. To discern the composition of
-  the monomer layers, addressing Question (\ref{point:monomernum}), we ran
+  the monomer layers, addressing question (\ref{point:monomernum}), we ran
   simulations of systems created with 4 - 8 monomers per layer. We built systems
@@
   ns of simulation. In a sense, all systems are at least metastable, addressing
-  Question (\ref{point:metastable}), however not all will make physical sense or fit
+  question (\ref{point:metastable}), however not all will make physical sense or fit
   the experimental profile that we are trying to match. Figure~\ref{fig:p2p}
@@
 
-  We answer Question (\ref{point:orientation}) by simulating X-ray diffraction
+  We answer question (\ref{point:orientation}) by simulating X-ray diffraction
   patterns produced from equilibrated MD trajectories. We tested systems built
@@
         \vspace{-0.2em}
-        \includegraphics[width=1.018\linewidth]{offset_rzplot.png}
+        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{offset_rzplot.png}
         \caption{}~\label{fig:rz_offset}
@@
 %        \vspace{0.25em}
-        \includegraphics[scale=0.29]{WAXS_raw.png}
+        \includegraphics[scale=0.285]{WAXS_raw.png}
         \caption{}~\label{fig:raw_waxs}
@@
         \centering
-        \includegraphics[width=\linewidth]{layered_rzplot.png}
+        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{layered_rzplot.png}
         \caption{}~\label{fig:rz_layered}
@@
         \vspace{-4.00em}
-        \includegraphics[width=\linewidth]{colorbar_jet.png}
+        \includegraphics[width=\linewidth]{colorbar_seismic.png}
   \end{subfigure}
@@
 
+  In addition to R-$\pi$ being shifted to lower $\mathbf{q}$ values, a few
+  factors combine to make the simulated R-$\pi$ reflection visibly more intense
+  than in the experimental pattern. The simplest reason is that R-$\pi$ and
+  R-alkanes add together to boost the overall signal at interesecting values of
+  $\mathbf{q}$. In addition, we observe a much higher maximum intensity within
+  R-$\pi$. The maximum intensity within R-$\pi$ of the normalized experimental
+  pattern is 3.1, while the maximum intensity within R-$\pi$ of the normalized
+  parallel displaced simulated pattern is 32.9. While direct numerical
+  comparisons between simulation and experiment aren't necessarily precise due to
+  underlying assumptions, an order of magnitude difference suggests some
+  significance. We believe that we see such a high maximum for two reasons: (1)
+  We are simulating a perfectly aligned system so all X-rays reflected along the
+  pore axis would add constructively. The crystalline domains in the real system
+  are not perfectly aligned (See azimuthal distribution in supplemental
+  information) which would lead to an overall decrease in the intensity of
+  R-$\pi$. (2) Our system is more ordered with high correlation between layers.
+  We will come back to this point further in ensuing discussions.
+
+  There is a grid-like pattern near $\mathbf{q}=0$ which appears because the
+  simulated system shows crystalline character. The grid features along nonzero
+  values of $q_z$ line up with reflections at $q_z=0$ which indicates positional
+  correlations between columns in the z-direction. This type of correlation is
+  expected for a crystalline material. If our system met the definition of a
+  columnar liquid crystalline system, we should observe only weak short-range
+  z-directional correlation within columns, with no correlation between
+  columns\cite{chaikin_principles_1995}.
+
   The R-spots signal, which appears in both simulated XRD patterns, is not a
@@
   sit between tails of vertically stacked monomers rather than stacking directly
-  on top of them (Figure blah blah blah). This type of packing has been seen
+  on top of them (Figure~\ref{fig:hex_tails}). This type of packing has been seen
   before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.
@@
   \caption{We hypothesize that R-spots is the result of ordered tail packing.
-	  Defining the membrane plane to be 0\degree, we
-	  measured the angles between each alkane chain tail centroid and its nearest
-	  neighbor centroids for the equilibrated parallel displaced (a) and sandwiched
-	  (c) configurations. Peaks that appear in each distribution are centered near
-	  $\pm~33\degree$. We radially integrated the simulated XRD patterns of the
-	  parallel displaced and sandwiched configuration within the region bounding
-	  R-alkanes ((b) and (d) respectively).  Peaks appear in the same location as the
-	  angle distributions which corroborates our hypothesis. Further, we note that
-	  the peaks are strongest in both plots associated with the sandwiched
-	  configuration. As shown in Figure \ref{fig:rz_layered}, systems simulated in
-	  the sandwiched configuration exhibit more intense R-spots
-	  reflections.}~\label{fig:tail_packing}
+	  Defining the membrane plane to be 0\degree, we measured the angles between each
+	  alkane chain tail centroid and its nearest neighbor centroids for the
+	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
+	  that appear in each distribution are centered near $\pm~33\degree$. We radially
+	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
+	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
+	  Peaks appear in the same location as the angle distributions which corroborates
+	  our hypothesis. Further, we note that the peaks are strongest in both plots
+	  associated with the sandwiched configuration. As shown in Figure
+	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
+	  more intense R-spots reflections. Note that plots of integrated intensity are
+	  normalized so the average alkane intensity (excluding reflections $\pm
+	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
+	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
+  \end{figure}
+
+%BJC: not sure if this figure is necessary
+  \begin{figure}
+	\centering
+	\includegraphics[width=0.5\linewidth]{hexagonal_tails_alt2.png} 
+	%BJC: I can give the circle some depth if that makes it clearer
+	\caption{Monomer tails prefer to pack in a hexagonal array. Each circle
+		represents a monomer tail as seen if viewed by looking from the end of the tail
+		to the pore center. Each color represents distinct monomers from adjacent
+		layers.}~\label{fig:hex_tails}
   \end{figure}
@@
 
-  We learned that layers are well-defined and persistent, answering Question
+  We learned that layers are well-defined and persistent, answering question
   (\ref{point:layers}). We established our conclusion by plotting the two
@@
   configuration, suggesting that we have found another metastable free energy
-  basin, further corroborating Question (\ref{point:metastable}). 
+  basin, further corroborating question (\ref{point:metastable}). 
   %The basins are
@@
   between R-spots and R-alkanes fades (Figure~\ref{fig:offset_disordered_xrd}).
-  In the sandwiched configuration, R-spots is weakly present, but in different
-  locations, showing higher intensity at the top and bottom of the pattern as
-  well as at the intersection of R-alkanes with q$_z$ = 0
+  In the sandwiched configuration, R-spots is present, but there are only two
+  spots located at the intersection of $q_z=0$ with R-alkanes.
   (Figure~\ref{fig:layered_disordered_xrd}).
@@
                 \centering
-                \includegraphics[width=\linewidth]{offset_disordered_rzplot.png}
+                \includegraphics[width=\linewidth]{disorder_offset_rzplot.png}
                 \caption{}~\label{fig:offset_disordered_xrd}
@@
                 \centering
-                \includegraphics[width=\linewidth]{layered_disordered_rzplot.png}
+                \includegraphics[width=\linewidth]{disorder_rzplot.png}
                 \caption{}~\label{fig:layered_disordered_xrd}
@@
                 \caption{Sandwiched, Ordered Pore Basin}~\label{fig:sandwich_xy}
-        \end{subfigure}%
+        \end{subfigure}
         \begin{subfigure}{0.47\linewidth}
@@
                 \caption{Sandwiched, Disordered Pore Basin}~\label{fig:disorder_sandwich_xy_correlation}
-       \end{subfigure}%
+       \end{subfigure}
        \begin{subfigure}{0.47\linewidth}
@@
 	  disorder when initial configuration layer stacking distance is increase from
-	  3.7\AA~ to 5\AA~apart.}\label{fig:xy_correlation}
+	  3.7 \AA~to 5 \AA~apart.}\label{fig:xy_correlation}
   \end{figure}
@@
   \subsection{Slow dynamics}
-
-  %BJC: Matt thinks this section is necessary
 
@@
 
-  In order to address Question (\ref{point:poredefinition}), we plotted the
+  In order to address question (\ref{point:poredefinition}), we plotted the
   number densities of heavy atoms in the head group, carbon atoms in the tail
@@
 
-  We explored the affect of water on pore structure, addressing Question
+  % BJC: I'm not sure this section is necessary anymore. The original point was to 
+  % see if we get more structure. It's not clear this is the right way to introduce
+  % water into the system. I think it confuses things.
+
+  We explored the affect of water on pore structure, addressing question
   (\ref{point:water}), by preparing parallel displaced and sandwiched
@@
   	\rowname{Parallel Displaced}&
-  	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_1.png}&
-  	\includegraphics[width=.28\linewidth]{solvated_offset_rzplot_25.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
   	\includegraphics[width=.325\linewidth]{solvated_offset_rzplot_5.png}\\[-1ex]
@@
   	\rowname{Sandwiched}&
-  	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_1.png}&
-  	\includegraphics[width=.28\linewidth]{solvated_layered_rzplot_25.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_1.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
   	\includegraphics[width=.325\linewidth]{solvated_layered_rzplot_5.png}\\[-1ex]
@@
   (Fig.~\ref{fig:IC_xlink}).
-
-  %BJC: add units
+  %BJC: The current XRD pattern is from a 100 ns simulation. I am running it out
+  % longer to get more statistics
+
   \begin{figure}
@@
   per layer and an initial layer spacing of 3.7 \AA.
-  % MRS4: do we have a sense of how consistent this behavior is? I.e. if
-  % started with 4 apart does it look like 3.7 or 5 separations? How about 4.5?
-  % Is there a gradual range of changes? Can we rule this out? What work was
-  % done on this?
-  % BJC3: I'll get back to you
 

### 2018-02-23 Ben_Manuscripts/structure_paper/supplemental.tex
New figures, updated figures, text edits on draft and supplemental

@@
 	The net charge on the monomer is input as -1 since the sodium ion is kept as 
-	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools_nodate} and the
+	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools16_2016} and the
 	output of \texttt{antechamber} to create Amber topology files. A detailed
@@
 	\item We calculated the time when each of the pore-to-pore distances
-	were equilibrated using \texttt{pymbar.timeseries.detectEquilibration()} \\
+	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
 	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
@@
 	\caption{There are five pore-to-pore distances that are equal in a perfect
-		hexagonal. If each number in the diagram represents the center of a
+		hexagon. If each number in the diagram represents the center of a
 		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
@@
 	\fontsize{14pt}{12pt}\selectfont
-	\textbf{\noindent Experimental correlation length of R-$\pi$}
+	\noindent \textbf{Experimental correlation length of R-$\pi$}
   \endgroup
@@
   L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
-  of the diagonal entry of the covariance matrix calculated 
+  of the diagonal entry of the covariance matrix of optimized fit paramaters. 
   % need citations and more on lorentzian parameters
@@
 	  the pores squeeze together, but in a distorted hexagonal array because the xy
-	  translation of the pores is somewhat erratic.
+	  initial translation of the pores is somewhat erratic.
 
@@
 
-	  \item Initial distance between layers
+	  \item \underline{Initial distance between layers}
 
@@
 
+  \begin{figure}
+	\centering
+	\includegraphics[width=0.75\linewidth]{nematic_director.png}
+	\caption{We define the nematic director vector, $\mathbf{n}$, as the vector
+	perpendicular to the plane of the aromatic head group.}~\label{fig:director}
+  \end{figure}
+
   \begin{figure}[ht]
@@
   \end{subfigure}
-  \caption{}~\label{fig:nematic_distribution}
+  \caption{The distribution of angles between nematic director vector (See
+	  Figure~\ref{fig:director}) and the z-axis averaged over the equilibrated portion
+	  of each trajectory}~\label{fig:nematic_distribution}
   \end{figure}
@@
 	\centering
+	\includegraphics[width=0.75\linewidth]{radial_distribution_annulus.png}
+	\caption{Looking down onto the plane of membrane, this diagram
+		illustrates how we calculated radial distribution
+		functions. We binned the radial distance of all atoms in 
+                chosen groups from pore centers. The pore centers are 
+                defined as the average coordinates of sodium ions in each
+                pore. The bins are defined by the annulus bounded by concentric
+		circles centered at the pore centers, as shown. To normalize, we
+		divide the count of atoms within the bin annulus by the volume of
+                the annulus where the volume is the area of the annulus times the
+                height of the membrane in the z-direction.}~\label{fig:rdf_diagram}
+  \end{figure}
+
+  \begin{figure}
+  \centering
         \begin{subfigure}{0.45\textwidth}
@@
 \clearpage
-\bibliography{llc.bib}
+\bibliography{llc}
 \end{document}

### 2018-02-27 Ben_Manuscripts/structure_paper/Draft.tex
Some more comments.

@@
 
+%MRS5: could be punchier. I will keep thinking.  I should be the last author.  Chen the names that Joe and Matt wanttu use (presumably with some middle initial?
 \title{Understanding the nanoscale structure of hexagonal phase lyotropic 
@@
 \author{Benjamin J. Coscia}
-\author{Michael R. Shirts}
-\email{michael.shirts@colorado.edu}
 \author{Richard D. Noble}
@@
 \affiliation{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
-
+\author{Michael R. Shirts}
+\email{michael.shirts@colorado.edu}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
 \begin{document}
@@
   recover useful compounds.
+
+%MRS6: I would keep a paragraph about here how current membranes DON'T
+%work for this purpose. But one paragraph is enough.x
 
@@
   inherently exhibit high selectivity due to their strict molecular weight
-  cut-off (MWCO) ~\cite{zhou_supported_2005}. Additionally, the LLC monomers
-  chosen to make membranes for this application are salts, and therefore lead to
+  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
+  %MRS6:
+  described in this paper
+  %chosen to make membranes for this application 
+  are salts, and therefore lead to
   Donnan exclusion of ions in solution. The membrane gains a net surface charge
@@
 
-  The H\textsubscript{II} phase pore geometry is better for transport than the
+  The H\textsubscript{II} phase pore geometry is 
+%MRS6:
+%better 
+has a higher theoretical capacity
+for transport than the
   Q\textsubscript{I} phase. The H\textsubscript{II} phase forms at room
@@
 
-  Our current understanding of LLC membrane systems is not rich enough to be
+  Our current understanding of 
+%MRS6:
+the molecular details of
+LLC membrane 
+%systems 
+nanostructure
+is not 
+%MRS6: 
+%rich enough to be
+sufficient
   able to precisely design them for specific separations. Over the past 20 years,
@@
 	\end{subfigure}
+%MRS6: this is one place where I might go to passive voice, since anyone can only speculate not just us.  
   \caption{We can only speculate about solute behavior inside the membrane
-	  pores based on our previous picture of the pore structure (a). We will use a
+	  pores based on our previous picture of the pore structure (a). 
+%MRS6: should be present text, not ``will use'' since it's what's happening in this paper. Look for this throughout.
+          We will use a
 	  detailed molecular model in order to appropriately model the pore's complex
@@
 	  transport (b). The head group region is colored blue
+%MRS6: probably mention from actual simulations we will describe below.
 	  and the tail region is colored cyan in both representations.}~\label{fig:detail}
@@
 
-  \item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}
-
+%MRS6: formatting suggestion
+  \item \textit{If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}} 
   A simple molecular simulation study of a similar molecule suggested that
@@
 
-  \item How do monomers in each layer position themselves with respect to
-  surrounding layers? \label{point:orientation}
-
+  \item \textit{How do monomers in each layer position themselves with respect to
+  surrounding layers? \label{point:orientation}}
   $\pi$-$\pi$ stacking interactions between aromatic monomer head groups may be
@@
 
-  \item Does our model support the existence of layers and if so, how well
-  defined are the layers? \label{point:layers}
-
+  \item \textit{Does our model support the existence of layers and if so, how well
+  defined are the layers? \label{point:layers}} 
   %BJC: Reordered, so changing the wording here.
@@
 
-  \item Can the system exist in other metastable states or phases that are not
-  accessed during experiments? \label{point:metastable}
-
+  \item \textit{Can the system exist in other metastable states or phases that are not
+  accessed during experiments? \label{point:metastable}}
   There remains the possibility that there is more than one metastable state
@@
   trapped in a metastable free energy basin. We must be able to identify which
-  state is produced experimentally.
-
-  \item What constitutes a pore, and what are the details of its pore architecture? \label{point:poredefinition}
-
+  states 
+  %MRS6: best not to set up too high expectations
+  %is produced experimentally.
+  are most consistent with experiment.
+
+  \item \textit{What constitutes a pore, and what are the details of its pore architecture? \label{point:poredefinition}}
   The limited picture that experiment provides tells us that there are
@@
 
-  \item Is it necessary to include any water in order to appropriately model
-  the Col\textsubscript{h} phase? \label{point:water}
-
+  \item \textit{Is it necessary to include any water in order to appropriately model
+  the Col\textsubscript{h} phase? \label{point:water}}
   While past work describes the Col\textsubscript{h} phase as dry~\cite{feng_scalable_2014}, 
@@
 	\item \textit{R-$\pi$}: The location of the first is at $q_z$ = 1.7
-	\AA$^{-1}$, corresponding to a real space separation of 3.7 \AA~. Previous
+	\AA$^{-1}$, corresponding to a real space separation of 3.7 {\AA}. Previous
 	work~\cite{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
@@
 	relative intensity.  Accordingly, we name these reflection R-spots. The
-	location of all spots is $\sim 37$ degrees from the $q_z$ axis in their
+	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
 	respective quadrants. In many liquid crystal systems one can explain the spots
@@
   (Figure~\ref{fig:python}).
-
+  %MRS6: question; we would like to make these releasable in GitHub.
   \begin{figure}
@@
 	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
-		configuration. (b) A python script rotates and assembles monomers into layers with 
+		configuration. (b) A Python script rotates and assembles monomers into layers with 
 		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
@@
   a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
-  configurations. The initial distance between pores also has little effect on
-  the the equilibrated structure However, one should not start them too close or
+  configurations. 
+  %MRS6: added.
+  The initial distance between pores, within a wide range, also has little effect on
+  the the equilibrated structure. However, one should not start them too close or
   there will be high energy repulsions during early equilibration. We chose an
@@
   of 4.12 nm.  A sensitivity analysis of both parameters is presented in
-  the supplemental information.  The distance between layers, the rotation of the
+  the 
+  %MRS6: check for J phys chem B to see if its supporting or supplemental information or material.
+  supplemental information.  The distance between layers, the rotation of the
   layers with respect to adjacent layers, and the number of monomers per layer do
@@
   headgroups in the parallel displaced initial configuration stack with an offset
-  of $180/nmon$ degrees where $nmon$ equals the number of monomers per layer. See
+  of $180^\circ/nmon$ where $nmon$ is the number of monomers per layer. See
   the Supplemental Information for a detailed illustration of the initial
@@
 
-  In order to create a wet system, we solvated an initial configuration with
+  %MRS6: some parameters missing here (time run between insertions, etc). 
+  %I assume they are in supporting information?
+  In order to create a ``wet'' system, we solvated an initial configuration with
   water using \texttt{gmx solvate}. We remove all water molecules placed outside
@@
   \begin{equation}
-	 S = \frac{1}{2} \langle(3cos^2\theta -1)\rangle
+	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
 	\label{eqn:nematic_order_parameter}
@@
   quantifying the degree of monomer head group alignment between systems. We use
-  Equation~\ref{eqn:nematic_order_parameter} to accomplish this by defining
+  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
   $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
@@
   the monomer layers, addressing question (\ref{point:monomernum}), we ran
-  simulations of systems created with 4 - 8 monomers per layer. We built systems
+  simulations of systems created with 4--8 monomers per layer. We built systems
   in both the parallel displaced and sandwiched configurations with layers
@@
   according to the dry equilibration procedure. All systems are stable after 400
-  ns of simulation. In a sense, all systems are at least metastable, addressing
+  ns of simulation. 
+  %MRS6: Above, probably need to be a bit more clear what you mean by stable (no noticable drift in pore-to-pore), and if you are only using data after the point of stability.
+In a sense, all systems are at least metastable, addressing
   question (\ref{point:metastable}), however not all will make physical sense or fit
   the experimental profile that we are trying to match. Figure~\ref{fig:p2p}
-  shows the pore spacing for all systems tested. Systems built with 5 monomers in
+  shows 
+%MRS6:
+%the pore spacing 
+the equilibrated pore-to-pore distances 
+for all systems tested. 
+Systems built with 5 monomers in
   each layer equilibrate to a pore spacing that is most consistent with the
   experimental value of 4.12 nm derived from SAXS measurements
-  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the
+  (Figure~\ref{fig:SAXS}). 
+%MRS6: discuss very briefly how far off 4 and 6 are to motivate selecting 5 exclusively.
+The remainder of this discussion will focus on the
   analysis of systems built with 5 monomers per layer.
@@
 	\includegraphics[width=\linewidth]{p2p.png}
-	\caption{When we build systems with 5 monomers per layer , the
-		equilibrated pore spacing is closest to the experimental value of 4.12 nm. The
+        %MRS6: should there be a grapical demonstration of sandwiched vs. parallel displaced, especially equilbrated?
+        %MRS6: some tweaks below.
+	\caption{Systems with 5 monomers per layer have
+		equilibrated pore spacing closest to the experimental value of 4.12 nm. The
 			equilibrated pore spacing of the model increases as the number of monomers in
@@
   is $2\times$R-$\pi$~away. 
-
   %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
@@
   \end{subfigure}
+%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced.
+Any thoughts why?
+We can discuss in person.
+And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
+%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
   \caption{The simulated XRD pattern generated from the equilibrated trajectory
@@
   model systems that contain $\pi$ interactions in a classical mechanical context
-  using polarizable forcefields \cite{baker_polarizable_2015}. We could
-  implement a polarizable force field, however it is likely not worth the extra
-  computational cost. If our model proves to be inadequate when simulating
-  transport, we will revisit our current choice of forcefield.
+  using polarizable forcefields \cite{baker_polarizable_2015},
+  %MRS6: 
+  but they are significantly more computationally expensive to
+  reach the time scales required to equilibrate these systems at the present time.
+  %MRS6: not so relevant below.
+  %We could
+  %implement a polarizable force field, however it is likely not worth the extra
+  %computational cost. If our model proves to be inadequate when simulating
+  %transport, we will revisit our current choice of forcefield.
 
@@
   pattern is 3.1, while the maximum intensity within R-$\pi$ of the normalized
-  parallel displaced simulated pattern is 32.9. While direct numerical
+  parallel displaced simulated pattern is 32.9. 
+  %MRS2 10x is really big.
+That seems hard to actually manage .
+.
+.
+I didn't realize it was that big.
+For some reason, I thought it was around 3x.
+If it's that big, how come the 7.4 A reflection isn't big?
+It's not clear to me how this is possible.
+Not clear how the angle averaging obscured this before?
+  While direct numerical
   comparisons between simulation and experiment aren't necessarily precise due to
@@
   correlations between columns in the z-direction. This type of correlation is
-  expected for a crystalline material. If our system met the definition of a
+  expected for a crystalline material. 
+%MRS6: need some justification for why we are not totally surprised the system is crystalline.
+But is is so crystalline in the x direction?
+The grid spacing is ``crystalline-ish'' in both x and z directions.
+.
+.
+we should talk.
+If our system met the definition of a
   columnar liquid crystalline system, we should observe only weak short-range
@@
 	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
+  %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
   \end{figure}
@@
         %BJC3: The scaling is the same
+        %MRS6: OK, I'm seeing this new light.
+the HUGE intensity in the simulation is from the carbon of the tail, not the pi-pi.
+There isn't anything like that in the experimental in the alkane region.
+What happens if you remove a couple of more carbons from the tails?
+Does this has something to do with the stacking of alkane tails in the z direction?
+is that not experimentally observed?
+I need to think through this a bit more .
+.
+.
+I maybe missing something obvious having to do with require correlations between the stacking of the tails and the stacking of the pi.
+Maybe normalizing by the tails is NOT the right thing to do, because in the z direction, stacked pi interactions lead to stacked tails at the same distance (a requirement of the molecules being connected, so if that stacking is different between experiment and theory, it leads to different intensities.
+On the other hand, if the experiment had tails that are stacked together at 3.7 A on average, it seems like they would have to be much flatter to fit.
+Hmmm.
+What do the aromatics signals alone look like?
+(i.e.
+the opposite of 9a).
+I need to think .
+.
+.
   \end{figure}
@@
 
-%BJC: not sure if this figure is necessary
+%BJC: not sure if this figure is necessary.  
+%MRS6: kind of confusing with just the circles and no molecules to hang them on.
   \begin{figure}
@@
 
+%MRS6: should probably be present tense.  Maybe phrase ``in our simulations, layers are'' 
   We learned that layers are well-defined and persistent, answering question
@@
   decay in their intensity as z increases. We do not see correlation between
+%MRS6: correlations of what between pores?
   pores, however correlations within pores are strong throughout the length of
@@
   \end{subfigure}
+  %MRS6: have the same color scale in both figures to compare them?
   \caption{2D pair distribution functions generated from systems built in the 
@@
 	   configuration}\label{fig:yz_correlation}
+%MRS6: caption not finished?
   \end{figure}
@@
 
+  %MRS6: do you need both the 2D and 1D correlation functions?
   \begin{figure}
@@
   copies of the system.
+
+%MRS6: not sure if we WANT to do this, but could do a simulation with 2x as many layers and see if the correlation changes.
 
@@
   in closer agreement with experiment. WHY IS THIS BOLD??!}~\label{table:nematic}
+%MRS6: for some reason, might be set in the jpcbfk package?
   \end{table}
@@
   \subsection{Slow dynamics}
-
+%MRS6: Is the fact that it's lyotropic relevant? 
   We observe unusually slow dynamics in our system. Typical diffusion constants
@@
 
+%MRS6: I don't know that the equilibration procedure induces it; I doubt a metastable state would have slower kinetics than the real state. It might be the force field is too stable. 
   It is possible that our equilibration procedure may induce glassy phase
@@
   model with the closest match to experimental data.
-
+%MRS6: don't need a table if all the same.
   \begin{table}[h]
@@
 
+%MRS: I think you will need to refer back to names of the questions (or at least shortened versions of the names): people skimming the paper will not remember what the numbers are.
   In order to address question (\ref{point:poredefinition}), we plotted the
@@
 
-  \subsection{Affect of Water on Structure}
+  \subsection{Effect of Water on Structure}
 
@@
   % water into the system. I think it confuses things.
+
+  %MRS6: good question.  It is interesting to see the swelling. We can talk.
 
@@
 
+%MRS6: I think we should remove the ``we learned'', and express it more in terms of the observed facts: rather than ``we learned statement X'', you can just say ``statement X''.
+Or ``observation Y in the simulations supports the conclusion Y''.
   We have used a detailed molecular model of the Col\textsubscript{h} phase
@@
 
+%MRS6'' isn't it 1-3 orders of magnitude lower?
+You cite some slower statistics, and there might be differences between lyotrpic and thermotropic, if the hydrophilic/hydrophobic effect is stronger than the effects in thermotropic fluids.
   We acknowledge that our simulated system exhibits glassy dynamics. The

### 2018-02-28 Ben_Manuscripts/structure_paper/Draft.tex
got correct version back

@@
   configuration from the trajectory which we used for full system
-  construction (Figure~\ref{fig:python}a). See supplemental information for
+  construction (Figure~\ref{fig:python}a). See Supporting Information for
   further detail.
@@
   %MRS6: question; we would like to make these releasable in GitHub.
+  %BJC2: yes .. what is the question?
   \begin{figure}
@@
   %MRS6: check for J phys chem B to see if its supporting or supplemental information or material.
-  supplemental information.  The distance between layers, the rotation of the
+  %BJC2: good point. It is 'supporting information'
+  Supporting information.  The distance between layers, the rotation of the
   layers with respect to adjacent layers, and the number of monomers per layer do
@@
   \AA, however it shows non-physical behavior which is detailed in the 
-  Supplemental Information.
+  Supporting Information.
 
@@
   of $180^\circ/nmon$ where $nmon$ is the number of monomers per layer. See
-  the Supplemental Information for a detailed illustration of the initial
+  the Supporting Information for a detailed illustration of the initial
   configurations in each mode.
@@
   %I assume they are in supporting information?
+  %BJC2: Not there yet but will add
   In order to create a ``wet'' system, we solvated an initial configuration with
@@
   ions in their respective pores. We generated pore spacing statistics 
-  using the bootstrapping technique (See Supplemental Information).
+  using the bootstrapping technique (See Supporting Information).
 
@@
   $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
-  the aromatic head groups. See the supplemental information for a diagram.
+  the aromatic head groups. See the Supporting Information for a diagram.
 
@@
   from the pore centers, then normalized by the volume of the annulus defined by
-  the bin edges and the z box vector (See supplemental information for a 
+  the bin edges and the z box vector (See Supporting Information for a 
   diagram).
@@
   %MRS6: Above, probably need to be a bit more clear what you mean by stable (no noticable drift in pore-to-pore), and if you are only using data after the point of stability.
+  %BJC2: I believe this is included in methods. I can restate if that's not clear
 In a sense, all systems are at least metastable, addressing
@@
 %MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
+%BJC2: Sure, I'll add that to supporting info
   \caption{The simulated XRD pattern generated from the equilibrated trajectory
@@
 Not clear how the angle averaging obscured this before?
+  %BJC2 From plots of raw structure factor, it doesn't seem like a normalization issue. It was probably obscured in the orginal angle averaging because it 
+  % was averaged with neighboring bins
   While direct numerical
@@
   pore axis would add constructively. The crystalline domains in the real system
-  are not perfectly aligned (See azimuthal distribution in supplemental
-  information) which would lead to an overall decrease in the intensity of
+  are not perfectly aligned (See azimuthal distribution in Supporting
+  Information) which would lead to an overall decrease in the intensity of
   R-$\pi$. (2) Our system is more ordered with high correlation between layers.
@@
   %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
+  %BJC2: good idea
   \end{figure}
@@
 %MRS6: should probably be present tense.  Maybe phrase ``in our simulations, layers are'' 
-  We learned that layers are well-defined and persistent, answering question
+  In our simulations, layers are well-defined and persistent, answering question
   (\ref{point:layers}). We established our conclusion by plotting the two
@@
 		cases, the head group region has a higher degree of layer partitioning than the
-		tail region. (See supplemental information for detailed definitions of the head
+		tail region. (See Supporting information for detailed definitions of the head
 		group and tail regions)}\label{fig:zdf}
@@
   from experimental evidence. The experimental correlation length (See
-  supplemental information for details its derivation) suggests that layers are
+  Suppporting Information for details its derivation) suggests that layers are
   correlated with about 3 neighboring layers which is closer to the values
@@
 %MRS6: not sure if we WANT to do this, but could do a simulation with 2x as many layers and see if the correlation changes.
+%BJC2: have one that is 3x going right now
 
@@
   \textbf{n} and vectors orthogonal to monomer phenyl rings are presented in the
-  supplemental material. In general, ordered pore basin systems are more
+  Supporting Information. In general, ordered pore basin systems are more
   nematically ordered than disordered pore basin systems and sandwiched
@@
   region, we used the carbon atoms making up the aromatic ring. For the tail
-  region we used only carbon atoms of the monomer tails (See Supplemental
+  region we used only carbon atoms of the monomer tails (See Supporting
   Information for diagram). We average the histograms over at least 50 ns of

### 2018-03-01 Ben_Manuscripts/structure_paper/supplemental.tex
removed unneeded files

@@
 		columns are able to repel resulting in a large jump in pore spacing
-		(Figure~\ref{fig:p2p_39}). After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
-		There is a large uncertainty in this value because the 1-4 pore spacing
-		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
-		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
-		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
-                towards cubic packing.
+		(Figure~\ref{fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
+%		There is a large uncertainty in this value because the 1-4 pore spacing
+%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
+%		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
+%		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
+%                towards cubic packing.
 
@@
 		repulsion of columns once the restraining potential is switched to 56 KJ
-		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). After 400 ns, the
-		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
-		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
-		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
-		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
-		spacings is 3.96 nm.
+		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
+%		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
+%		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
+%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
+%		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
+%		spacings is 3.96 nm.
 
 		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
-		than the experimental value. We observe relatively stable pore spacing during
-		the restrained portion of the dry equilibration procedure
-		(Figure~\ref{fig:p2p_45}). The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
-		The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
-		pore spacing. We chose to use this value for all our simulations in the main
-		text.
+		than the experimental value. This systems exhibits the smallest response to our 
+ 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
+                value for all our simulations in the main text.
+f		%The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
+		%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
+		%pore spacing. We chose to use this value for all our simulations in the main
+		%text.
 
-		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \% larger than the
-		experimental value. Once the restraining potential reaches 56 KJ mol$^{-1}$
-		nm$^{-2}$, the pore spacing begins to decrease linearly (Figure~\ref{fig:p2p_50}).
-		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm. There is a large
-                uncertainty with this value because, again, the array of pores deviates from 
-                hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
-                2 drifts outward from the array and forces the 1-4 distance to shrink in 
-                response.
+		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \%
+		larger than the experimental value. Once the restraining potential reaches 56
+		KJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
+		a linear trend (Figure~\ref{fig:p2p_50}).
+%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
+%		There is a large
+ %               uncertainty with this value because, again, the array of pores deviates from 
+ %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
+  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
+   %             response.
 
@@
 		avoiding a system such as this where vacuum gaps between pore columns are
-		introduced unnecessarily. The system equilibrates to a pore spacing of 4.27
-		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
-                spacing of 3.99 \AA~ which distorts the hexagonal array.
+		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
+%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
+ %               spacing of 3.99 \AA~ which distorts the hexagonal array.
 

### 2018-03-02 Ben_Manuscripts/structure_paper/diffraction.tex
New diffraction things

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

\title{Understanding missing diffraction reflections}

\begin{document}

\graphicspath{{./figures/}}  % put all the figures here
\maketitle

Initial configurations are built in two ways: Parallel displaced and Sandwiched
(Figure ~\ref{fig:initial_configs}).  The simulated diffraction patterns for
equilibrated systems started in each configuration at 300 K are shown in Figure
~\ref{fig:xrd}. We observe stronger features in the alkane chain region when
the temperature is lowered to 280K (Figure~\ref{fig:xrd_280}). At both
temperatures we are missing what appears to be a subharmonic located at
($q_r=0$,$q_z=0.85$) in the experimental pattern. We would like to know 
why it doesn't appear -- whether it has something to do with our system
or the math behind the simulated structure factor itself.

\begin{figure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{sandwichedlayers.png}
                \caption{Sandwiched}\label{fig:sandwichedlayers}
        \end{subfigure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{offsetlayers.png}
                \caption{Parallel Displaced}\label{fig:offsetlayers}
        \end{subfigure}
	\caption{}\label{fig:initial_configs}
\end{figure}

\begin{figure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{rzplot_layered_300K.png}
                \caption{Sandwiched}\label{fig:xrd_layered}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{rzplot_offset_300K.png}
                \caption{Parallel Displaced}\label{fig:xrd_offset}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{WAXS_raw.png}
                \caption{Experiment}\label{fig:xrd_exp}
        \end{subfigure}
	\caption{}\label{fig:xrd}
\end{figure}

\begin{figure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{layered_rzplot.png}
                \caption{Sandwiched}\label{fig:xrd_layered}
        \end{subfigure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{offset_rzplot.png}
                \caption{Parallel Displaced}\label{fig:xrd_offset}
        \end{subfigure}
	\caption{}\label{fig:xrd_280}
\end{figure}

The hypothesis is that the subharmonic appears due to the reflection located at
($q_r=0,q_z$=1.7) in the experimental pattern. This reflection likely appears
because aromatic rings of monomer head groups pi-stack on top of each other
3.7~\AA apart. The subharmonic does not appear in our simulated patterns and
we need a good explanation for why that is the case. I explored fourier
transforms in various dimensions to help increase my understanding.

I first looked at the 1D case. I spaced delta functions 3.7 units (I'll call
the units angstroms for simplicity) apart. I adjusted the real space resolution
by increasing the number of points between delta functions.

\begin{figure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_highres.png}
                \caption{Real space - high resolution}\label{fig:real_delta_1d_highres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_medres.png}
                \caption{Real space - medium resolution}\label{fig:real_delta_1d_medres}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_lowres.png}
                \caption{Real space - low resolution}\label{fig:real_delta_1d_lowres}
	\end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_highres.png}
                \caption{Fourier space - high resolution}\label{fourier_delta_1d_highres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_medres}
                \caption{Fourier space - medium resolution}\label{fourier_delta_1d_medres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_lowres}
                \caption{Fourier space - low resolution}\label{fourier_delta_1d_lowres}
        \end{subfigure}
	\caption{Less subharmonics are present as resolution decreases}\label{fig:1D_deltas}
\end{figure}

Next, I replaced the delta function with gaussian functions. It turns out, the
number of subharmonics is dependent on the real space resolution and the width
of the gaussian. A larger sigma value leads to less subharmonics
(Figure~\ref{fig:1D_fourier_sigma}). The same trend seen in
Figure~\ref{fig:1D_deltas} is observed as real space resolution is increased
for a given sigma. That is, more subharmonics appear as resolution increases.
In the context of stacked benzene rings I would expect a more disordered system
to have less subharmonics. It is also possible to miss out on subharmonics if
the real space resolution is too small (i.e. data is binned into too large of
bins).

None of these subharmonics would actually show up in the experimental pattern
(except maybe the first one) because the wavelength of the X-rays is too large
(1.54 \AA). And there are no subharmonics corresponding to a real space
separation greater than 3.7 \AA. In order for the 7.4 \AA reflection to show
up, rings need to be spaced 7.4 \AA vertically. Then there would be a 3.7 \AA
subharmonic which shows up as the $\pi$-stacking reflection. In all plots,
subharmonics are always weaker in intensity than the fundamental frequency. 
So the question remains, why is the $\pi$-stacking reflection stronger than
the 7.4 \AA reflection?

\begin{figure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_highsig.png}
                \caption{Real space - sigma = 1}\label{fig:real_gauss_1d_highsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_medsig.png}
                \caption{Real space - sigma = 0.1}\label{fig:real_gauss_1d_medsig}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_lowsig.png}
                \caption{Real space - sigma = 0.001}\label{fig:real_gauss_1d_lowsig}
	\end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_highsig.png}
                \caption{Fourier space - sigma = 1}\label{fourier_gauss_1d_highsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_medsig}
                \caption{Fourier space - sigma = 0.1}\label{fourier_gauss_1d_medsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_lowsig}
                \caption{Fourier space - sigma = 0.001}\label{fourier_gauss_1d_lowsig}
        \end{subfigure}
	\caption{Using high real space resolution (same as Figure~\ref{1D_deltas}), it
                 is evident that a smaller sigma leads to more subharmonics. As sigma
		 approaches zero, the behavior is the fourier transform resembles that
		 of delta functions. Otherwise, the fourier transform of a gaussian is
		 a gaussian.}\label{fig:1D_gauss_sigma}
\end{figure}

Next, I explored 2D fourier transforms of grids of data that somewhat resemble 
the LLC system. I created parallel columns of points spaced 3.7\AA~apart. Each
point is represented as a 2-dimensional gaussian function. In Figure~\ref{fig:2d_columns_simple}
I show examples of simple configurations made up of one and two columns.

\begin{figure}
	\begin{subfigure}{0.45\textwidth}
	        \centering
                \includegraphics[width=\textwidth]{real_2d_1column.png}
                \caption{Real space - $\sigma_x=\sigma_y$ = 0.001}\label{fig:real_2d_1column}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_2column.png}
                \caption{Real space - $\sigma_x=\sigma_y$ = 0.001}\label{fig:real_2d_2column}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_1column.png}
                \caption{Fourier space}\label{fig:fourier_2d_1column}
	\end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_2column.png}
                \caption{Fourier space}\label{fourier_2d_2column}
        \end{subfigure}
	\caption{A single column of equispaced scatterers shows up as horizontal lines
		 with spacing equal to the inverse of the distance between scatters. Adding
		 a second column (b) causes the horizontal lines to become dots spaced apart
		 by the inverse of the distance between columns. Adding more columns would
                 follow the same trend.}~\label{fig:2d_columns_simple}
\end{figure}

Next, I explored columns with points spaced 7.4 \AA apart.
Figure~\ref{fig:2d_columns_offset} shows the fourier transform of a single
column. In Figure~\ref{fig:fourier_2d_74_1column} we see that the intensity of
each parallel line is about the same. Recall that the line corresponding to the
fundamental frequency (7.4 \AA real space) needs to be weaker in intensity than
its first subharmonic in order to be consistent with experiment. Turns out, we
can choose values of $\sigma_x$ and $\sigma_y$ that make this happen. If we 
change $\sigma_y$=0.4, we observe a faded effect at high frequency values. In this
way we would observe the $\pi$-stacking reflection as more intense than the 
7.4\AA reflection. It is also important that $\sigma_x$ stays low, otherwise, the
reflection disappears from the middle (Figure~\ref{fig:fourier_2d_74_1column_highxysig}).

\begin{figure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_74_1column.png}
                \caption{Real space - $\sigma_x$=$\sigma_y$=0.1}\label{fig:real_2d_74_1column}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_74_1column.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_74_1column_highysig.png}
                \caption{Real space - $\sigma_x$=0.1, $\sigma_y$=0.4}\label{fig:real_2d_74_1column_highysig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_74_1column_highysig.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column_highysig}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_1column_74_highxysig.png}
                \caption{Real space - $\sigma_x$=0.4, $\sigma_y$=0.4}\label{fig:real_2d_1column_75_highxysig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_1column_74_highxysig.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column_highxysig}
        \end{subfigure}

        \caption{A single column of scatterers spaced 7.4 \AA apart shows up as horizontal lines
                 with spacing equal to the inverse of the distance between scatters. One of the
                 subharmonics corresponds to a real spacing distance of 3.7 \AA. If we adjust the 
	         sigmas of the scattering, we can change the relative intensity of each
                 horizontal line in fourier space.}~\label{fig:2d_columns_offset}
\end{figure}

\end{document}

### 2018-03-06 Ben_Manuscripts/structure_paper/diffraction.tex
updates

@@
 temperatures we are missing what appears to be a subharmonic located at
-($q_r=0$,$q_z=0.85$) in the experimental pattern. We would like to know 
+($q_r=0$, $q_z=0.85$) in the experimental pattern. We would like to know 
 why it doesn't appear -- whether it has something to do with our system
@@
 
-\begin{figure}
+\begin{figure}[h]
         \begin{subfigure}{0.475\textwidth}
@@
 
-\begin{figure}
+\begin{figure}[h]
         \begin{subfigure}{0.33\textwidth}
@@
 The hypothesis is that the subharmonic appears due to the reflection located at
-($q_r=0,q_z$=1.7) in the experimental pattern. This reflection likely appears
+($q_r=0, q_z$=1.7) in the experimental pattern. This reflection likely appears
 because aromatic rings of monomer head groups pi-stack on top of each other
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\begin{subfigure}{0.45\textwidth}
@@
         \end{subfigure}
-
         \caption{A single column of scatterers spaced 7.4 \AA apart shows up as horizontal lines
@@
 
+And now I move into 3D. The only difference in its calculation is that I use
+\texttt{numpy.fft.fftn} instead of the 2D version. I come to the same
+conclusion as in the 2D case. Lines appear that are spaced apart by a distance
+equal to the inverse of the distance between points in the z direction
+(Figure~\ref{fig:fourier_3d_lowdig}).  If there is disorder in the z-direction
+(high $\sigma$) then lines at low z frequency fade
+(Figure~\ref{fig:fourier_3d_highzsig}). If there is disorder in the x (or y)
+direction, then intensity at low x frequencies fade
+(Figure~\ref{fig:fourier_3d_highysig}).
+
+\begin{figure}[h]
+	\centering
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{real_3d_lowsig.png}
+                \caption{Real space - $\sigma_z$=$\sigma_x$=$\sigma_y$=0.001}\label{fig:real_3d_lowsig}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{fourier_3d_lowsig.png}
+                \caption{Fourier space}\label{fig:fourier_3d_lowsig}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{real_3d_highzsig.png}
+                \caption{Real space - $\sigma_z$=0.5, $\sigma_x$=$sigma_y$=0.001}\label{fig:real_3d_highzsig}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{fourier_3d_highzsig.png}
+                \caption{Fourier space}\label{fig:fourier_3d_highzsig}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{real_3d_highysig.png}
+                \caption{Real space - $\sigma_z$=$sigma_y$=0.001, $\sigma_x$=0.5}\label{fig:real_3d_highysig}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{fourier_3d_highysig.png}
+                \caption{Fourier space}\label{fig:fourier_3d_highysig}
+        \end{subfigure}
+        \caption{A single column of scatterers spaced 7.4 \AA apart in 3D space shows up as horizontal lines
+                 with spacing equal to the inverse of the distance between scatters. One of the
+                 subharmonics corresponds to a real spacing distance of 3.7 \AA. If we adjust the
+                 sigmas of the scattering, we can change the relative intensity of each
+                 horizontal line in fourier space.}~\label{fig:3d_simple}
+\end{figure}
+
+The patterns are interesting, but they still don't fully explain the features.
+The main problem is that the lines fade starting from the center (0 frequency)
+of the fourier transform. They are quite strong at high frequency and very low
+at zero. We see the opposite in the experimental pattern.
+
+To address the problem, we need to make a more complicated system. So I'll
+start by adding more columns and packing them hexagonally
+(Figure~\ref{fig:hex_simple}). The dots of the dashed lines in the fourier
+transform (Figure~\ref{fig:fourier_3d_hex_lowsig}) are spaced apart by the
+inverse of distance between columns. If we add some uncertainty to the 
+locations of the points in the columns, we see fading of low frequencies
+as before. Interestingly, the pattern at x=0 does not fade despite the 
+x/y uncertainties being as high as in Figure~\ref{fig:fourier_3d_highysig}. 
+I'd need to do more to verify this, but it appears that the center does
+not fade in the x direction as long as the uncertainty in the xy directions
+is larger than the z direction.
+
+\begin{figure}[h]
+        \centering
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{real_3d_lowsig.png}
+                \caption{Real space - $\sigma_z$=$\sigma_x$=$\sigma_y$=0.001}\label{fig:real_3d_hex_lowsig}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{fourier_3d_hex_lowsig.png}
+                \caption{Fourier space}\label{fig:fourier_3d_hex_lowsig}
+        \end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{real_3d_hex_highsig.png}
+                \caption{Real space - $\sigma_x$=$sigma_z$=0.5, $\sigma_z$=0.8}\label{fig:real_3d_hex_highsig}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{fourier_3d_hex_highsig.png}
+                \caption{Fourier space}\label{fig:fourier_3d_hex_highsig}
+        \end{subfigure}
+
+	\caption{}\label{fig:hex_simple}
+\end{figure}
+
+The original problem still persists after putting in more columns. That is, the
+intensity of the horizontal lines at high frequencies is never lower than the
+value at low frequency. Angle averaging helps resolve this
+(Figure~\ref{fig:fourier_hex_angle_average}). With a little parameter tweaking,
+it looks even better (Figure~\ref{fig:fourier_hex_angle_average_better}). There 
+are still some high intensity areas at high frequency values. It is possible 
+those would go away in more complicated systems.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{fourier_hex_angle_average.png}
+		\caption{Fourier space - $\sigma_x$=$\sigma_z$=0.5, $\sigma_z$=0.8}\label{fig:fourier_hex_angle_average}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{fourier_hex_angle_average_better.png}
+		\caption{Fourier space - $\sigma_x$=$\sigma_z$=0.5, $\sigma_z$=0.8}\label{fig:fourier_hex_angle_average_better}
+	\end{subfigure}
+
+	\caption{Angle averaging the same pattern shown in Figure~\ref{fig:fourier_3d_hex_highsig} 
+	yields a pattern with the highest intensity concentrated at the center.}\label{fig:angle_averaged}
+\end{figure}
+
 \end{document}

### 2018-03-14 HII/Scripts/gentraj.py
3D fourier transforms of simple systems

@@ -289,30 +289,44 @@ if __name__ == "__main__":
     points = np.zeros([frames, npts, 3])  # will contain all positions for all frames
 
     # generate random points inside box
-    for t in tqdm.tqdm(range(frames)):
-        for i in tqdm.tqdm(range(npts)):
-            u, v, w = np.round(np.random.rand(3), decimals=4)  # generate 3 random numbers between 0 and 1
-            pt = O + u * A + v * B + w * C  # places point inside 3D box defined by box vector A, B and C
-            # if --pores, --layers or --disks is specified, check to make the random point is not in the region. If it
-            # is, keep generating random points until the point is outside the region
-            if args.pores:
-                while check_pores(pt, pore_locations, pore_radius):  # force all points outside the pore region
-                    u, v, w = np.random.rand(3)
-                    pt = O + u * A + v * B + w * C
-            if args.layers:  # force all points outside layer region
-                while check_layers(pt, layer_locations, args.layer_width):
-                    u, v, w = np.random.rand(3)
-                    pt = O + u * A + v * B + w * C
-            if args.disks:
-                while check_disks(pt, disk_locations, args.layer_width, disk_radius):
-                    u, v, w = np.random.rand(3)
-                    pt = O + u * A + v * B + w * C
-            if args.constrain_radius:
-                if i > 0:
-                    while spatial.cKDTree(points[t, :i, :]).query(pt)[0] < args.con_rad:
-                        u, v, w = np.random.rand(3)
-                        pt = O + u * A + v * B + w * C
-            points[t, i, :] = pt
+    # for t in tqdm.tqdm(range(frames)):
+    #     for i in tqdm.tqdm(range(npts)):
+    #         u, v, w = np.round(np.random.rand(3), decimals=4)  # generate 3 random numbers between 0 and 1
+    #         pt = O + u * A + v * B + w * C  # places point inside 3D box defined by box vector A, B and C
+    #         # if --pores, --layers or --disks is specified, check to make the random point is not in the region. If it
+    #         # is, keep generating random points until the point is outside the region
+    #         if args.pores:
+    #             while check_pores(pt, pore_locations, pore_radius):  # force all points outside the pore region
+    #                 u, v, w = np.random.rand(3)
[…]

### 2018-04-24 Ben_Manuscripts/structure_paper/Draft.tex
removed unneeded files
3D fourier transforms of simple systems
Edits and new figures

@@
 \usepackage{gensymb}
+\usepackage{xr}
+
+\makeatletter
+\newcommand*{\addFileDependency}[1]{% argument=file name and extension
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
+
+\newcommand*{\myexternaldocument}[1]{%
+    \externaldocument{#1}%
+    \addFileDependency{#1.tex}%
+    \addFileDependency{#1.aux}%
+}
+
+\externaldocument[S-]{supplemental}
 
@@
 \author{Joe Yelk}
-\author{Matthew Glaser}
+\author{Matthew A. Glaser}
 \affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
@@
   %takes steps towards solving.
+
+  Figure S~\ref{S-fig:monomer_color_coded}
 
@@
   %NF that motivate this research.
-  % BJC3: The point I am trying to make is that the way the membranes are made 
+  % BJC2: The point I am trying to make is that the way the membranes are made 
   % results in either low selectivity or low permeability. I could just state
@@
 
+%BJC3: reworded a lot of these to be more in line with Matt's way of thinking about LC systems
 %MRS6: formatting suggestion
-  \item \textit{If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}} 
+%  \item \textit{If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}} 
+  \item \textit{How many monomers pack around a single pore column?\label{point:monomernum}} 
   A simple molecular simulation study of a similar molecule suggested that
-  there are 4 monomers in each layer \cite{zhu_methacrylated_2006}. Their model
-  likely does not sufficiently imitate the chemical environment present in the
-  real system since it only contains 16 total monomers. A separate calculation
+  4 monomers radially pack around hydrophilic pore columns \cite{zhu_methacrylated_2006}.
+  Their model likely does not sufficiently imitate the chemical environment present
+  in the real system since it only contains 16 total monomers. A separate calculation
   for NA-GA3C11, based on the estimated volume of the liquid crystal monomers,
-  proposes that each layer consists of seven
+  proposes that each pore is surrounded by seven
   monomers\cite{resel_structural_2000}. Our best chance to answer this question
@@
   reported atomistic liquid crystal membrane simulation, as we present here. We
-  will directly change the layer composition and note its effect on membrane
-  structure.
-
-  \item \textit{How do monomers in each layer position themselves with respect to
-  surrounding layers? \label{point:orientation}}
+  will directly change the density of monomers in each pore and note its effect
+  on membrane structure.
+
+%  \item \textit{How do monomers in each layer position themselves with respect to
+%  surrounding layers? \label{point:orientation}}
+  \item \textit{In what orientation do monomer head groups stack on top of each
+  other \label{point:orientation} 
   $\pi$-$\pi$ stacking interactions between aromatic monomer head groups may be
@@
   Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking
-  attraction which favors the parallel displaced configuration in all cases
-  except where the substitutions are extremely electron
-  withdrawing\cite{waller_hybrid_2006,ringer_effect_2006}. In this study, we
-  compare simulated X-ray diffraction patterns to experiment in order to deduce
-  which stacking configuration is most likely. We also dive deeper into the
-  origin of features present in the 2D diffraction patterns.
-
-  \item \textit{Does our model support the existence of layers and if so, how well
-  defined are the layers? \label{point:layers}} 
-  %BJC: Reordered, so changing the wording here.
-  Indications of strong $\pi$-$\pi$ stacking interactions in the direction
-  perpendicular to the membrane plane, combined with the wedge-like character of
-  the LLC monomers, suggests that monomers should arrange into disks that stack in
-  layers. $\pi$-$\pi$ stacking will only occur between the aromatic
-  monomer head groups which leaves no description of what is happening in the
-  monomer tail region. The tails may entangle isotropically while maintaining
-  stacking order among headgroups.
-
-  \item \textit{Can the system exist in other metastable states or phases that are not
-  accessed during experiments? \label{point:metastable}}
-  There remains the possibility that there is more than one metastable state
-  associated with a given LLC phase. Simulating a membrane atomistically
-  requires many atoms which limits the timescales acessible with MD. It is
-  reasonable to expect that we will generate configurations which are kinetically
-  trapped in a metastable free energy basin. We must be able to identify which
-  states 
+  attraction which favors the parallel displaced configuration in all cases except
+  where the substitutions are extremely electron withdrawing  
+  \cite{waller_hybrid_2006,ringer_effect_2006}. We did not consider the T-shaped 
+  configuration due to its geometric incompatibility with a hexagonal columnar phase.
+  The entropic contribution of the long alkane tails should overwhelm any attraction
+  between aromatic head groups in the T orientation. We limit our studies to
+  comparison of systems built in the parallel displaced and sandwiched configurations.
+
+% BJC3: I don't want to limit X-ray diffraction patterns just to deciding between
+% parallel displaced and sandwiched. Since it doesn't actually decide either way.  
+%  In this study, we
+%  compare simulated X-ray diffraction patterns to experiment in order to deduce
+%  which stacking configuration is most likely. We also dive deeper into the
+%  origin of features present in the 2D diffraction patterns.
+
+%  \item \textit{Does our model support the existence of layers and if so, how well
+%  defined are the layers? \label{point:layers}}
+%  Indications of strong $\pi$-$\pi$ stacking interactions in the direction
+%  perpendicular to the membrane plane, combined with the wedge-like character of
+%  the LLC monomers, suggests that monomers should arrange into disks that stack in
+%  layers. $\pi$-$\pi$ stacking will only occur between the aromatic
+%  monomer head groups which leaves no description of what is happening in the
+%  monomer tail region. The tails may entangle isotropically while maintaining
+%  stacking order among headgroups.  
+% BJC3:rephrasing everything about the above question. 
+  \item \textit{How strong are stacking correlations between monomer head groups?
+  \label{point:layers}}
+
+%BJC3: Going to talk about temperature rather than ordered/disordered states
+%  \item \textit{Can the system exist in other metastable states or phases that are not
+%  accessed during experiments? \label{point:metastable}}
+%  There remains the possibility that there is more than one metastable state
+%  associated with a given LLC phase. Simulating a membrane atomistically
+%  requires many atoms which limits the timescales acessible with MD. It is
+%  reasonable to expect that we will generate configurations which are kinetically
+%  trapped in a metastable free energy basin. We must be able to identify which
+%  states 
   %MRS6: best not to set up too high expectations
   %is produced experimentally.
-  are most consistent with experiment.
-
-  \item \textit{What constitutes a pore, and what are the details of its pore architecture? \label{point:poredefinition}}
+%  are most consistent with experiment.
+
+  \item \textit{What constitutes a pore, and what are the details of its composition?
+  \label{point:poredefinition}}
   The limited picture that experiment provides tells us that there are
@@
 
-  \subsubsection{Number of monomer per layer}
+  \subsubsection{Density of monomers around pores}
 
@@
   initially spaced 3.7 \AA~apart. We prepared equilibrated configurations
-  according to the dry equilibration procedure. All systems are stable after 400
-  ns of simulation. 
-  %MRS6: Above, probably need to be a bit more clear what you mean by stable (no noticable drift in pore-to-pore), and if you are only using data after the point of stability.
-  %BJC2: I believe this is included in methods. I can restate if that's not clear
-In a sense, all systems are at least metastable, addressing
-  question (\ref{point:metastable}), however not all will make physical sense or fit
-  the experimental profile that we are trying to match. Figure~\ref{fig:p2p}
-  shows 
-%MRS6:
-%the pore spacing 
-the equilibrated pore-to-pore distances 
-for all systems tested. 
-Systems built with 5 monomers in
-  each layer equilibrate to a pore spacing that is most consistent with the
-  experimental value of 4.12 nm derived from SAXS measurements
+  according to the dry equilibration procedure. The pore-to-pore spacing is stable
+  in all systems are stable after 400 ns of simulation. Figure~\ref{fig:p2p} shows
+  the equilibrated pore-to-pore distances for all systems tested. Systems built 
+  with 5 monomers in each layer equilibrate to a pore spacing that is most consistent
+  with the experimental value of 4.12 nm derived from SAXS measurements 
   (Figure~\ref{fig:SAXS}).
-%MRS6: discuss very briefly how far off 4 and 6 are to motivate selecting 5 exclusively.
-The remainder of this discussion will focus on the
-  analysis of systems built with 5 monomers per layer.
+
+  The remainder of this discussion will focus on the analysis of systems built with
+  5 monomers per layer. Systems built with 6 monomers per layer have an equilibrated
+  pore spacing c.a. 0.50 nm higher than experiment. Systems built with 4 monomers per 
+  layer equilibrate to a pore spacing 0.25 nm lower than experiment. In a sense, all
+  systems tested are at least metastable, however not all will make physical
+  sense or fit the experimental profile that we are trying to match. In the limit of
+  infinite time, all simulations will converge to a single density. It is our 
+  intention to choose an initial configuration which quickly reaches a monomer density
+  close to experiment.
 
@@
         %MRS6: should there be a grapical demonstration of sandwiched vs. parallel displaced, especially equilbrated?
-        %MRS6: some tweaks below.
-	\caption{Systems with 5 monomers per layer have
-		equilibrated pore spacing closest to the experimental value of 4.12 nm. The
-			equilibrated pore spacing of the model increases as the number of monomers in
-			each layer increases. The pore spacing of systems starting in the sandwiched
-			configuration is systematically lower than those started in the parallel
-			displaced configuration.}~\label{fig:p2p}
+        % BJC3: I have that in the supplemental information. I could move it into the main
+        % body. I think it would be best in the intro where I pose the question of parallel 
+        % displaced v. sandwiched.
+	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
+			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
+			 increases as the number of monomers in each layer increases. The pore spacing
+			 of systems starting in the sandwiched configuration are systematically lower
+			 than those started in the parallel displaced configuration.}~\label{fig:p2p}
   \end{figure}
 
-  \subsubsection{Relative interlayer head group orientation}
-
-  We answer question (\ref{point:orientation}) by simulating X-ray diffraction
-  patterns produced from equilibrated MD trajectories. We tested systems built
-  with 5 monomers per layer in the parallel displaced and sandwiched
-  configurations. We generated simulated patterns using portions of simulation
-  trajectory after equilibration. The patterns for both structures are shown and
-  compared to experiment in Figure \ref{fig:XRDsim}.
+%  \subsubsection{Relative interlayer head group orientation}
+  \subsubsection{Structural refinement}
+
+  We further refined our structural understanding of the system by simulating X-ray 
+  diffraction patterns produced from equilibrated MD trajectories and comparing them
+  to experiment. We tested systems built with 5 monomers per layer in the parallel 
+  displaced and sandwiched configurations at 300K. We generated simulated patterns using 
+  portions of simulation trajectory after equilibration. The patterns for both 
+  structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
+
+  Simulated XRD of the sandwiched configuration shows most all experimental features 
+  except R-helix and R-spots. R-pores and R-alkanes appear in their expected locations. 
+  R-pores is more intense than experiment, likely because we are simulating a perfect,
+  infinite hexagonal array. The real system has defects and domain misalignment
+  which decreases the overall intensity. R-$\pi$ appears with very high intensity and
+  is shifted down to a lower value of $q_z$ meaning monomers in our model prefer to 
+  stack farther apart.
 
@@
 
-  The parallel displaced configuration results in a simulated XRD pattern with
-  the closest match to experiment. It produces the only pattern that exhibits all
-  major reflections. R-alkanes and R-pores appear as they do in the sandwiched
-  configuration. R-spots and R-$\pi$ appear, however with a lower intensity
+  Like the sandwiched configuration, the parallel displaced configuration creates
+  a simulated XRD pattern with all major experimental reflections except for R-helix.
+  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
+  and R-$\pi$ appear, however with a lower intensity
   relative to R-alkanes when compared to the sandwiched configuration. R-helix
@@
   this particular WAXS pattern as the product of tilted alkane
-  chains~\cite{feng_scalable_2014}. We measured the tilt angle of the alkane
-  chains and showed that our system equilibrates to an average tilt angle close
-  to zero degrees (Fig.~\ref{fig:tilt}). To understand the origin of R-spots,
-  we determined which atoms gave rise to the feature. Since R-spots is present as
-  higher intensity spots within R-alkanes, it is likely that the spots arise as a
-  consequence of the tails. By removing all non-tail atoms from the trajectory
-  and simulating a diffraction pattern, we were able to isolate the cause of the
-  spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat,
-  we plotted the centroids of the tails and measured the angle between each
-  centroid and its nearest neighbors with respect to the plane of the membrane.
-  We see distinct peaks in the distribution of these angles
-  (Figure~\ref{fig:tail_packing}).
+  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched
+  configuration since R-spots appears with the most strength in its simulated XRD
+  pattern. We measured the tilt angle of the alkane chains and showed that our
+  system equilibrates to an average tilt angle close to zero degrees
+  (Fig.~\ref{fig:tilt}). To understand the origin of R-spots, we determined which
+  atoms gave rise to the feature. Since R-spots is present as higher intensity
+  spots within R-alkanes, it is likely that the spots arise as a consequence of
+  the tails. By removing all non-tail atoms from the trajectory and simulating a
+  diffraction pattern, we were able to isolate the cause of the spots to the
+  tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
+  the centroids of the tails and measured the angle between each centroid and its
+  nearest neighbors with respect to the plane of the membrane.  We see distinct
+  peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).
 

### 2018-04-24 Ben_Manuscripts/structure_paper/Outline.tex
Edits and new figures

@@
 
-  \subsection*{Determination of Nanoscopic Structural Details}
+%  \subsection*{Determination of Nanoscopic Structural Details}
 
@@
 
-  We will now address the questions raised in the introduction in the order
-  that they were asked.  %BJC: Not a fan of this transition
+ % We will now address the questions raised in the introduction in the order
+  %that they were asked.  %BJC: Not a fan of this transition
 
@@
 
-  The simulations best support a model built with 5 monomers per layer based on 
-  the measured pore-to-pore distances. To discern the composition of the monomer 
-  layers, addressing (\ref{point:monomernum}), we ran simulations of systems created
-  with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
-  \begin{itemize}
-        \item We created systems in both the parallel displaced and sandwiched configurations
-	\item All systems were prepared according to the dry equilibration procedure
-        \item All systems are stable after 400 ns of simulation.  
-        \item Figure ~\ref{fig:p2p} shows the pore spacing for all systems tested.
-        \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
-        that is most consistent with the experimental value of 4.12 nm derived from
-        SAXS measurements (Figure~\ref{fig:SAXS}).
-        \item The remainder of this discussion will focus on the analysis of systems
-        built with 5 monomers per layer.
-  \end{itemize}
-
-  %BJC: maybe split into 2 paragraphs
-  %MRS2: usually good instinct.
-Lead with the conclusions of the research you are trying to convince readers.
-Rather than phrasing as a question.
-Something like: ``Layers are well defined and persistent''.
-  We learned that layers are well-defined and persistent, answering (\ref{point:layers})
-  %We verified that the system stays partitioned into layers by
-  We verified our conclusion by
-  plotting the pair correlation function, $g(z)$ calculated between atoms along
-  the length of the pores (Fig~\ref{fig:zdf}).
-  \begin{itemize}
-	\item We measured $g(z)$ with respect to aromatic rings in the head groups
-	and, separately, with respect to carbon atoms on the alkane chains.
-	% \item In both cases, we see a degree of layer partitioning
-        \item Using the head groups as reference, we see that sandwiched configuration
-	layers stack 4.29 \angstrom apart while parallel displaced configuration layers
-	stack 4.37 \angstrom apart.
-	\item Using the alkane chain carbons as reference we see a layer spacing of 4.39 \angstrom
-	and 4.38 \angstrom in the sandwiched and parallel displaced configurations respectively.
-        \item The power spectrums used to calculate the reported layer spacings are given in the 
-        Supplemental Information.  %BJC: "Power spectrum" an okay description here?
-	% BJC: TODO: Overlay plots of tail and headgroup densities
-        %MRS2: repore more precisely what finding is interesting. What does that difference mean?
-%	\item We see a difference in the spacing in the head group versus tail region
-%	because there is more volume to fill with less densely packed carbon chains in the tail region. 
-	% BJC: vvv Need to get the same information for the tail zdfs.
-%	\item Even though the layer spacing is similar, the sandwiched configuration
-%	exhibits more defined layers with its first peak deviating from the mean 
-%        number density by 61 \%. %BJC: I mention how I do this calculation in the methods. Is it clear that I'm doing that here?
-%MRS2: fine for description for now.          
-%	\item The parallel displaced configuration deviates from the mean by only 
-%	12 \% in comparison.
-%MRS2: is this that unexpected, since parallel displaces should have layers that alternate anyway?
-%BJC: true, but I'm just stating the facts
+  %BJC3: Feel free to suggest different words
+  \subsection{Density of monomers around pores}
+  Our simulations best support a model built with 5 monomers per layer based on
+  the measured equilibrated pore-to-pore distances. To discern the composition of
+  the monomer layers, addressing question (\ref{point:monomernum}), we ran
+  simulations of systems created with 4--8 monomers per layer. 
+  \begin{itemize}  
+  		\item We built systems in both the parallel displaced and sandwiched configurations 			with layers initially spaced 3.7 \AA~apart according to the dry equilibration 
+  		procedure.
+  		\item The pore-to-pore spacing is stable in all systems are stable after 400 ns of 
+  		simulation. Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all 
+  		systems tested. 
+  		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
+  		most consistent with the experimental value of 4.12 nm derived from SAXS measurements 
+	    (Figure~\ref{fig:SAXS}).
+  \end{itemize}
+
+  %  The simulations best support a model built with 5 monomers per layer based on 
+%  the measured pore-to-pore distances. To discern the composition of the monomer 
+%  layers, addressing (\ref{point:monomernum}), we ran simulations of systems created
+%  with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
+%  \begin{itemize}
+%        \item We created systems in both the parallel displaced and sandwiched configurations
+%	\item All systems were prepared according to the dry equilibration procedure
+%        \item All systems are stable after 400 ns of simulation.  
+%        \item Figure ~\ref{fig:p2p} shows the pore spacing for all systems tested.
+%        \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
+%        that is most consistent with the experimental value of 4.12 nm derived from
+%        SAXS measurements (Figure~\ref{fig:SAXS}).
+%        \item The remainder of this discussion will focus on the analysis of systems
+%        built with 5 monomers per layer.
+%  \end{itemize}
+
+  The remainder of this discussion will focus on the analysis of systems built with
+  5 monomers per layer. 
+  \begin{itemize}
+	  	\item Systems built with 6 monomers per layer have an equilibrated
+  		pore spacing c.a. 0.50 nm higher than experiment. 
+  		\item Systems built with 4 monomers per layer equilibrate to a pore spacing 0.25 nm 
+  		lower than experiment. 
+  		\item In a sense, all systems tested are at least metastable, however not all will make 
+  		physical sense or fit the experimental profile that we are trying to match.
+  		\item In the limit of infinite simulation time, all simulations will converge to a 	
+  		single density.
+  		\item It is our intention to choose an initial configuration which quickly reaches a 
+  		monomer density close to experiment.
   \end{itemize}
@@
 	\centering
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf5layered.png}
-                \caption{}\label{fig:zdf_layered}
-        \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf5offset.png}
-                \caption{}\label{fig:zdf_offset}
-        \end{subfigure}
-        \caption{Pair distribution functions of aromatic carbons for the
-        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
-        parallel displaced configurations. Clear periodic maxima in the
-        $z$ probability density indicate distinct layers. The magnitude
-        of the spikes with respect to the average suggest that the 5
-        monomer per layer, sandwiched configuration possesses a higher
-        degree of layer partitioning.}\label{fig:zdf}
+	\includegraphics[width=\linewidth]{p2p.png}
+	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
+			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
+			 increases as the number of monomers in each layer increases. The pore spacing
+			 of systems starting in the sandwiched configuration are systematically lower
+			 than those started in the parallel displaced configuration.}~\label{fig:p2p}
   \end{figure}
 
-  % BJC: Even though I will shift focus to only 5 monomers per layer, I will put other data
-  % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information 
-  %MRS2: good.
-  \begin{figure}
-	\centering
-	\includegraphics[width=0.5\linewidth]{p2p.png}
-	\caption{The pore spacing (given in nm) of the model increases as
-	number of monomers in each layer increases. The pore spacing of a system
-	starting in the sandwiched configuration is systematically lower than 
-	that started in an offset configuration. Systems built with 5 monomers
-	per layer in a parallel displaced configuration result in a pore spacing
-	closest to the experimental 4.12 nm}~\label{fig:p2p}
-  \end{figure}
-
+% BJC3: replaced by plot above.
 %  \begin{table}[h]
@@
 %  \end{table}
+
+  \subsection{Structural determination}
+
+  We further refined our structural understanding of the system by simulating X-ray 
+  diffraction patterns produced from equilibrated MD trajectories and comparing them
+  to experiment. 
+  \begin{itemize}
+	  	\item We tested systems built with 5 monomers per layer in the parallel 
+		displaced and sandwiched configurations at 300K.
+		\item We generated simulated patterns using portions of simulation trajectory
+		after equilibration.
+		\item The patterns for both structures are shown and compared to experiment
+		in Figure~\ref{fig:XRDsim}.
+  \end{itemize}
+
+%  Simulated XRD of the sandwiched configuration contains all experimental
+%  features except for R-helix. R-alkanes, R-spots and R-pores appear close to their
+%  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
+%  a $q_z$ value lower than experiment meaning the head groups in our model prefer 
+%  to stack farther apart.
+
+%  Like the sandwiched configuration, the parallel displaced configuration creates
+%  a simulated XRD pattern with all major experimental reflections except for R-helix.
+%  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
+%  and R-$\pi$ appear, however with a lower intensity
+%  relative to R-alkanes when compared to the sandwiched configuration. R-helix
+%  appears due to the parallel displaced aromatic rings. It is a subharmonic of
+%  R-$\pi$ since the nearest vertically stacked head group to any given head group
+%  is $2\times$R-$\pi$~away. 
+% BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
+
+% BJC3: update with 300K pics. Presented separately from 280K for now. 
+  \begin{figure}
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+        \vspace{-0.2em}
+        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_offset_300K.png}
+        \caption{}~\label{fig:rz_offset}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+%        \vspace{0.25em}
+        \includegraphics[scale=0.285]{WAXS_raw.png}
+        \caption{}~\label{fig:raw_waxs}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+        \centering
+        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_layered_300K.png}
+        \caption{}~\label{fig:rz_layered}
+  \end{subfigure}
+  \begin{subfigure}{0.0544\linewidth}
+        \centering
+        \vspace{-4.00em}
+        \includegraphics[width=\linewidth]{colorbar_seismic.png}
+  \end{subfigure}
+%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced.
+Any thoughts why?
+We can discuss in person.
+And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
+%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
+%BJC2: Sure, I'll add that to supporting info
+  \caption{The simulated XRD pattern generated from the equilibrated trajectory
+	  of the parallel displaced configuration (a) exhibits all major reflections
+	  present in the experimental WAXS pattern (b). The simulated XRD pattern
+	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
+	  all major reflections except R-helix.}
+  \label{fig:XRDsim}
+  \end{figure}
+
+  The simulated XRD patterns produced from both systems show moderate qualitative 
+  agreement with experiment. 
+  \begin{itemize}
+  		\item R-alkanes and R-pores appear in the expected location
+		\item R-pores is more intense than experiment, likely because we are simulating a 
+		perfect, infinite hexagonal array. The real system has defects and domain misalignment
+	    which decreases the overall intensity.
+	    \item R-$\pi$ appears at a lower $q_z$ value than experiment. In both systems, the
+	    reflection reaches its maximum at c.a. $q_z=1.4$ which means that monomers prefer 
+	    to stack c.a. 4.5 \AA apart rather than 3.7 \AA. This behavior is not surprising since
+	    GAFF models atoms as point charges and does not appropriately model the aromatic
+	    $\pi-\pi$ interactions which would cause the monomers to stack closer together.
+	    \item R-spots is missing in both places, at least visually. The tails in our model
+	    are more disordered than the experimental system at 300K.  
+	    \item R-helix does not appear in either case.
+  \end{itemize}
+
+  The simulated XRD pattern of the parallel displaced configuration shows an additional
+  reflection due to its helical structure. 
+  \begin{itemize}
+  		\item There are horizontal reflections at $|q_z|= 0.7 \AA^{-1}$, exactly half of 
+  		the $q_z$ value of R-$\pi$. 
+  		\item The reflection does not cross through $q_r = 0 \AA^{-1}$ so it does not
+  		appear for the same reason as R-helix. 
+  		\item It is possible that these reflections contribute to the continuation of
+  		R-helix into R-alkanes, as seen in the experimental pattern. 
+  \end{itemize}
+
+  There are numerical discrepancies between the relative intensities of each reflection when
+  comparing experimental and simulated patterns.
+  \begin{itemize}
+  		\item Table~\ref{table:relative_inensities_300K} quantifies the relative intensity
+  		of each reflection.
+  		\item The intensity of R-spots is much lower than experiment (need to update the numbers in that table with 300K results)
+  		\item There is no R-helix intensity
+  		\item R-$\pi$ is nearly an order of magnitude higher in our simulations
+  		compared to experiment.
+  \end{itemize}
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cccc}
+  \toprule
+  		   & \multicolumn{3}{c}{Configuration} \\
+  \hline
+  Reflection & Experiment & Sandwiched & Parallel Displaced \\
+  \midrule
+  R-alkanes & 1.0 &  1.0 &  1.0  \\  
+  R-$\pi$   & 2.8 & 18.0 & 14.0  \\
+  R-spots   & 1.5 &  1.6 &  1.2  \\  % Need to get these actual data points
+  R-helix   & 0.9 &  --  & --    \\ 
+  \bottomrule
+  \end{tabular}
+  \caption{The relative intensities of reflections of interest}
+  \label{table:relative_inensities_300K} 
+  \end{table}
+
+%  The simulated XRD pattern produced from the sandwiched configuration is missing
+%  R-helix and R-spots. 
+%  \begin{itemize}
+%		\item R-pores and R-alkanes appear in their expected locations. 
+%		\item R-pores is more intense than experiment, likely because we are simulating a 
+%		perfect, infinite hexagonal array. The real system has defects and domain misalignment
+%	    which decreases the overall intensity.
+%	    \item R-$\pi$ appears with a very high intensity and is shifted down to a lower value
+%	    of $q_z$ meaning monomers in our model prefer to stack farther apart.  
+%	    \item R-spots may be faintly present, however it is not present to the degree shown
+%	    experimentally. (see table with relative intensities) 
+%  \end{itemize}
+
+  %BJC: discussed parallel displaced and sandwiched configs in separate paragraphs to 
+  % avoid confusion. Need to make thesis less dry. 
+%  The simulated XRD pattern generated from the parallel displaced configuration is also
+%  missing R-helix and R-spots.
+%  \begin{itemize}
+%  		\item R-pores and R-alkanes appear in the expected location again
+%  		\item R-$\pi$ is present in the same location as the sandwiched configuration with
+%  		high intensity. 
+%  		\item R-helix is not present, however off-axis reflections appear at the same value 
+%  		of $q_z$ where we expect to see R-helix. These appear since there is a helical 
+%  		arrangement of monomers in the parallel displaced configuration. A helix alone will
+%  		not give rise to a reflection at $q_r = 0$ (See supporting info for demonstration)
+%  		\item There is elevated intensity where we expect to see R-spots, however it cannot
+%  		be easily distinguished from the higher intensity arcs which overlay the top and 
+%  		bottom of R-alkanes.
+%  \end{itemize}
+
+%  The simulated diffraction patterns indicate that there is something going wrong
+%  with the way the system is modeled. We must address all of these issues and justify
+%  their occurrence.
+  There are clear differences between our simulated results and experimental results
+  that must be addressed and justified. We will explore the origin of each experimental 
+  reflection and hypothesize why they do not appear in our simulated patterns. Specifically,
+  we want answer:  
+  %BJC: I could number these and answer them individually
+  \begin{enumerate}
+	\item What is the origin of R-spots?
+  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
+  	\item What is the origin of R-helix?
+  \end{enumerate}
+
+  \subsubsection{Origin of R-spots}
+
+  We observed R-spots when we ran simulations of each system at 280K. (figure to be added - include with 300K patterns or keep separate??)
+  \begin{itemize}
+  		\item R-spots is most intense in the sandwiched configuration
+  		\item Still no R-helix
+  \end{itemize}
+
+  %BJC: might be able to combine with other table
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cccc}
+  \toprule
+  		   & \multicolumn{3}{c}{Configuration} \\
+  \hline
+  Reflection & Experiment & Sandwiched & Parallel Displaced \\
+  \midrule
+  R-alkanes & 1.0 &  1.0 &  1.0  \\  
+  R-$\pi$   & 2.8 & 27.0 & 119.0  \\
+  R-spots   & 1.5 &  1.6 &  1.2  \\  
+  R-helix   & 0.9 &  --  & --    \\ 
+  \bottomrule
+  \end{tabular}
+  \caption{The relative intensities of reflections of interest}
+  \label{table:relative_inensities_300K} 
+  \end{table}
+
+  %BJC3: following taken from draft.tex
+  The R-spots signal, which appears in both simulated XRD patterns, is not a
+  result of alkane chain tilt. Previous literature has attributed the spots in
+  this particular WAXS pattern as the product of tilted alkane
+  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched
+  configuration since R-spots appears with the most strength in its simulated XRD
+  pattern. We measured the tilt angle of the alkane chains and showed that our
+  system equilibrates to an average tilt angle close to zero degrees
+  (Fig.~\ref{fig:tilt}).
+
+  %BJC3: from draft.tex  
+  To understand the origin of R-spots, we determined which
+  atoms gave rise to the feature. Since R-spots is present as higher intensity
+  spots within R-alkanes, it is likely that the spots arise as a consequence of
+  the tails. By removing all non-tail atoms from the trajectory and simulating a
+  diffraction pattern, we were able to isolate the cause of the spots to the
+  tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
+  the centroids of the tails and measured the angle between each centroid and its
+  nearest neighbors with respect to the plane of the membrane.  We see distinct
+  peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
+  \caption{We measured the angle made between each monomer alkane tail and the
+	  membrane plane. The average tilt angle is near 7\degree~which is far from the
+	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
+  %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
+  %BJC2: good idea
+  \end{figure}
+
+  The peaks in the nearest neighbor angle distribution are consistent with the
+  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
+  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
+  location where the highest intensity of spots are located on the simulated
+  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
+  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
+  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
+  \degree$, in close agreement with the previously measured angle distribution
+  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
+  performed the same integration on the raw experimental data and found the angle
+  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
+  is a reconcilable difference with our simulated results.
+
+%  The evidence supports the hypothesis that alkane chain tails pack in a
+%  hexagonal array. Groups of three tails associated with each monomer prefer to
+%  sit between tails of vertically stacked monomers rather than stacking directly
+%  on top of them (Figure~\ref{fig:hex_tails}). This type of packing has been seen
+%  before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.
+
+  \begin{figure}
+	\centering
+	\begin{subfigure}{0.45\linewidth}
+		\centering
+	 	\vspace{-2em}
+		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
+		\caption{}\label{fig:topdown_tails_only}
+	\end{subfigure}
+	\begin{subfigure}{0.45\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{tails_rzplot.png}
+		\caption{}\label{fig:tails_rzplot}
+	\end{subfigure}
+	\caption{(a) We removed all atoms except carbon atoms that constitute the tails from a 
+	sandwiched configuration trajectory. (b) The simulated XRD pattern of the
+        tail-only trajectory still shows R-spots}\label{fig:tails}
+  \end{figure}
+
+  \begin{figure}[!htb]
+  \centering
+  	\begin{subfigure}{\linewidth}
+	\centering
+		\begin{subfigure}{0.45\textwidth}
+        		\centering
+        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
+        		\caption{}~\label{fig:offset_tails}
+		\end{subfigure}
+		\begin{subfigure}{0.45\textwidth}
+		\centering
+	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
+		        \caption{}~\label{fig:offset_integration}
+		\end{subfigure}
+	\end{subfigure}
+	\begin{subfigure}{\linewidth}
+	\centering
+		\begin{subfigure}{0.45\textwidth}
+	        \centering
+		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
+		        \caption{}~\label{fig:layered_tails}
+		\end{subfigure}
+		\begin{subfigure}{0.45\textwidth}
+        	\centering
+		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
+		        \caption{}~\label{fig:layered_integration}
+		\end{subfigure}
+	\end{subfigure} 
+    \caption{We hypothesize that R-spots is the result of ordered tail packing.
+	  Defining the membrane plane to be 0\degree, we measured the angles between each
+	  alkane chain tail centroid and its nearest neighbor centroids for the
+	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
+	  that appear in each distribution are centered near $\pm~33\degree$. We radially
+	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
+	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
+	  Peaks appear in the same location as the angle distributions which corroborates
+	  our hypothesis. Further, we note that the peaks are strongest in both plots
+	  associated with the sandwiched configuration. As shown in Figure
+	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
+	  more intense R-spots reflections. Note that plots of integrated intensity are
+	  normalized so the average alkane intensity (excluding reflections $\pm
+	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
+	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
+  \end{figure}
+
+  There are a couple reasons why we see ordered chain packing at 280 K and not at the
+  experimental conditions of 300 K.
+  \begin{itemize}
+  		\item (1) The difference between 280K and 300K is small. Our forcefield parameters
+  		may not correctly model the behavior of the tails at 300K (citation?).
+  		\item (2) Monomers aren't as confined at 300 K in our simulations versus experiment.
+  		If the head groups packed 3.7 \AA apart, the tails would be more confined and forced
+  		to pack between vertically adjacent monomer tails. In our case, the tail region is
+  		less dense than experiment which gives the tails freedom to organize in a more
+  		entropically favored disordered state. 
+  \end{itemize}
+
+% BJC3 : old outline
+% R-spots, which appears in both simulated XRD patterns, is a result of the way 
+%  alkane tails pack together.
+%  \begin{itemize}
+%  	\item Previously, the spots in the diffraction pattern had been explained 
+%	as the product of tilted alkane chains. % BJC: reference 2014 ACS nano paper
+%	\item We measured the tilt angle of the alkane chains and showed that our 
+%	system equilibrates to an average tilt angle close to zero degrees ~\ref{fig:tilt} % Could belong in supplemental. Leaving here for now 
+%	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
+%	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
+%        that the spots arise as a consequence of the tails. 
+%	\item By removing atoms from the trajectory and simulating a diffraction 
+%	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails}).
+%	\item Since the tails stay nearly flat, we plotted the centroids of the 
+%	tails and measured the angle between each centroid and its nearest neighbors
+%	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).  %BJC: at one point Matt mention doing a correlation function instead of just measuring the angles
+%	\item We see distinct peaks in the distribution of these angles (Figure~\ref{fig:tail_packing})
+%  \end{itemize}
+%
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
+%  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
+%  indicates an average tilt angle near 7\degree which is far from the 37\degree tilt angle 
+%  previously used to explain R-spots}~\label{fig:tilt}
+%  \end{figure}
+%
+%  The peaks in the tilt angle distribution are consistent with the location of R-spots.
+%  \begin{itemize}
+%	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
+%	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
+%	of spots are located on the simulated patterns
+%	\item We confirmed this conclusion by radially integrating the 2D WAXS pattern for q values
+%	between 1.57 and 1.4 (real space between 4 and 4.5 \AA) 
+%	\item We observe that distinct peaks appear c.a. 30 $\degree$, in close agreement with the
+%	previously measured angle distribution (~\ref{fig:offset_integration}~\ref{fig:layered_integration})
+%%	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
+%	\item We performed the same integration on the raw experimental data and found the angle
+%	at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a 
+%	reconcilable difference with our simulated results.  
+%  \end{itemize}
+%
+%  \begin{figure}
+%	\centering
+%	\begin{subfigure}{0.45\linewidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
+%		\caption{}\label{fig:topdown_tails_only}
+%	\end{subfigure}
+%	\begin{subfigure}{0.45\linewidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{tails_rzplot.png}
+%		\caption{}\label{fig:tails_rzplot}
+%	\end{subfigure}
+%	\caption{(a) All atoms except carbon atoms making up the tails are removed from the 
+%	trajectory. (b) The simulated diffraction pattern of the tail-only trajectory still 
+%        shows R-spots}\label{fig:tails}
+%        %MRS2: might need to say how the dynamic range is adjusted here with only tails, since otherwise people will be confused with the R-spots being more intense. 
+%	%BJC: what do you mean by dynamic range?
+%	%BJC: Explain how colorbar is adjusted
+%  \end{figure}
+% 
+%
+%  \begin{figure}
+%  \centering
+%  	\begin{subfigure}{\linewidth}
+%	\centering
+%		\begin{subfigure}{0.45\textwidth}
+%        		\centering
+%        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
+%        		\caption{}~\label{fig:offset_tails}
+%		\end{subfigure}
+%		\begin{subfigure}{0.45\textwidth}
+%		\centering
+%	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
+%		        \caption{}~\label{fig:offset_integration}
+%		\end{subfigure}
+%	\end{subfigure}
+%	\begin{subfigure}{\linewidth}
+%	\centering
+%		\begin{subfigure}{0.45\textwidth}
+%	        \centering
+%		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
+%		        \caption{}~\label{fig:rz_layered}
+%		\end{subfigure}
+%		\begin{subfigure}{0.45\textwidth}
+%        	\centering
+%		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
+%		        \caption{}~\label{fig:layered_integration}
+%		\end{subfigure}
+%	\end{subfigure}
+%%MRS: 
+%  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
+%  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
+%  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
+%  (b) and (d) respectively.}~\label{fig:tail_packing}
+%%MRS2: not clear what the difference is between right and left side figures.
+%%BJC: That's good! One is angles measured between tail centroids and the other is radial integration of the simulated xrd patterns. I'll try make that more clear in the caption.
+%%MRS3: sorry, I meant to say not clear what the SOURCE of the data is in right vs. left.  Make sure colors and labels are consistent in final 
+%%MRS: not clear why some are angles with x axis, and some are angles w neighbors?  Shouldn't it be the same thing plotted in both graphs?
+%%BJC: I just need to get the labels right, they are the same thing technically
+%  \end{figure}
+
+  \subsubsection{Discrepancies between R-$\pi$}
+
+  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
+  of mass of monomer phenyl rings (Figure reference).
+  \begin{itemize}
+  		\item We averaged all 1D slices in the z-direction of the full 3D correlation function
+  		within 2.1 \AA of $(x, y)=(0, 0)$. (full description will be in methods)
+  		\item We chose 2.1 \AA as a crude approximation of the radius of the phenyl ring
+  		plane. 
+  		\item We calculated it as the sum of the longest C-C distance within a phenyl 
+  		ring (2.8 \AA) and two times the carbon atom radius (0.7 \AA).
+  \end{itemize}
+
+  The correlation length between stacked monomer head groups shows the best agreement with
+  experiment for systems simulated at 300K.
+  %BJC3: explanation of correlation length calculation in methods section. 
+  \begin{itemize}
+  		\item Correlation length was calculated by fitting a decaying exponential function
+  		to all peaks of $g(z)$ for the sandwiched configuration and to every other peak of
+  		$g(z)$ for the parallel displaced configuration. 
+  		\item The correlation length of systems simulated at 280K were 27.7 \AA and 25.2 \AA
+  		for the parallel displaced and sandwiched configurations respectively. 
+  		\item The correlation length of systems simulated at 300K were 11.2 \AA and 14.9 \AA
+  		for the parallel displaced and sandwiched configurations respectively. 
+  		\item Systems simulated at 300K show correlation closest to the experimental 
+  		correlation length of 10.1 \AA. They are still slightly more correlated than 
+  		experiment which would lead to an increase in constructive X-ray scattering. 
+  \end{itemize}
+
+  Additionally, our system models near-perfectly straight pores with no defects which will
+  lead to higher intensity vertical stacking reflections. 
+  \begin{itemize}
+  		\item Nearly all of the intensity in R-$\pi$ of our simulated patterns is concentrated
+  		at a single point. Figure Something shows the same simulated patterns with the upper 
+  		boundary on the colorbar adjusted to be 10x higher. The only visible reflections are
+  		those of R-$\pi$.
+  		\item In the experimental pattern, the intensity is more evenly spread out over all
+  		of R-$\pi$. 
+  \end{itemize}
+
+  \subsubsection{Origin of R-helix}
+
+  R-helix will not show up in any of the models tested so far.
+  \begin{itemize}
+        \item All monomers used to build initial configurations are identical. There is no way 	
+        to produce R-helix without a more complex initial configuration 
+        \item We calculated the structure factor of simple systems that mimic the parallel
+        displaced and sandwiched configurations. Neither give rise to R-helix.
+        (See Figure "fourier transforms of simple systems").
+        \item The reflection implies a vertical modulation in electron density every 7.4 \AA.                
+        \item This modulation can occur in either the head or the tails
+        \item There is a not a unique solution to this problem, however we can speculate based
+        on what makes the most physical sense.
+  \end{itemize}
+
+  We can produce R-helix if our initial configuration contains alternating parallel and
+  antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
+  (Figure reference).  
+  \begin{itemize}
+  		\item It is difficult to physically justify this system. 
+  		\item Systems built this way are only stable if position restraints are placed on 
+  		all head group heavy atoms. Carboxylate groups quickly revert to the parallel
+  		position as restraints are released.
+  		\item There is an appreciable energy barrier that prevents rotation
+  		of carboxylate groups attached to phenyl rings since the group extends the system's 
+  		$\pi$ conjugation. (citation)
+  		\item There are instances where carboxylates in other systems rotate out of plane.
+  		\item Bushey et al. showed that bulky carbonyl-containing substituents of stacked arene
+  		molecules tended to tilt 45$\degree$ in order to relieve steric strain, thus allowing 
+  		$\pi$-stacking between molecules, and to hydrogen bond with neighboring molecules. 
+  		\item Lorenzo and Gra\~{n}a found 3 stable dimers of gallic acid (from which the 
+  		monomer, NA-GA3C11 was derived) with adenine. In all cases, the carboxylate group 
+  		remained planar, even with evidence of hydrogen bonding between the carboxyl group
+  		and nitrogen atoms of adenine. 
+  		\item The monomers which we are studying have no opportunities to hydrogen bond and 
+  		are confined so that any rotation about the phenyl-carboxylate bond would be sterically
+  		hindered. 
+  \end{itemize}
+
+  We can also produce R-helix if layers are not uniformly spaced. Rather, monomers might form 
+  pairs that stack less than 3.7 \AA apart, and whose center of masses are spaced 7.4 \AA 
+  from the next pair of monomers.(Figure reference)
+  \begin{itemize}
+  		\item To our knowledge, there have been no studies that specifically address the 
+  		possibility of a configuration like this. 
+  		\item Our forcefield causes our system to tend towards uniformly spaced layers. 
+  		\item As expected, simulations of this type of system are only stable if position
+  		restraints are applied to heavy atoms of the phenyl rings.
+  		\item Many \textit{ab initio} studies have measured the equilibrium distance between
+  		dimers of benzene and substituted benzene.
+  		\item Tauer and Sherrill explored the binding energies of tetramers of benzene, but
+  		did not explore the report the equilibrium distance between benzene rings. 
+  		\item Even if there have been other studies of the equilibrium distance between 
+  		stacks of benzene rings, it still does not model our system which has many 
+  		electron-withdrawing groups and bulky substituents that would likely affect stacking
+  		preferences. 
+  \end{itemize}
+
+  Our final hypothesized configuration which produces R-helix focus on the orientation of the
+  tails. 
+  \begin{itemize}
+  		\item In this configuration, monomers are rotated so that the vector created by the  
+  		bond extending from the carboxylate carbon to the phenyl ring is oriented $\pm 15 	
+  		\degree$ with respect to the vector extending from the carboxylate carbon to the pore
+  		center.
+  		\item Every other monomer layer is rotated $+15 \degree$ and those in between are
+  		rotated $-15 \degree$.
+  		\item This configuration allows monomer tails to sit between adjacent monomer tails 
+  		which may be the most favorable way for them to pack. 
+  		\item This configuration is stable short-term while unrestrained.
+  		\item This may be the most reasonable explanation for the appearance of R-helix. The
+  		long-term stability of a configuration similar to this may be feasible if monomers
+  		stay stacked 3.7 \AA apart. 
+  \end{itemize}
+
+   %BJC3: 6 panel figure. Top 3 show each real space configuration in 3D. Bottom 3 show their
+   % simulated XRD patterns.
+
+  %BJC: maybe split into 2 paragraphs
+  %MRS2: usually good instinct.
+Lead with the conclusions of the research you are trying to convince readers.
+Rather than phrasing as a question.
+Something like: ``Layers are well defined and persistent''.
+%  We learned that layers are well-defined and persistent, answering (\ref{point:layers})
+  %We verified that the system stays partitioned into layers by
+%  We verified our conclusion by
+%  plotting the pair correlation function, $g(z)$ calculated between atoms along
+%  the length of the pores (Fig~\ref{fig:zdf}).
+%  \begin{itemize}
+%	\item We measured $g(z)$ with respect to aromatic rings in the head groups
+%	and, separately, with respect to carbon atoms on the alkane chains.
+	% \item In both cases, we see a degree of layer partitioning
+        %\item Using the head groups as reference, we see that sandwiched configuration
+%	layers stack 4.29 \angstrom apart while parallel displaced configuration layers
+%	stack 4.37 \angstrom apart.
+%	\item Using the alkane chain carbons as reference we see a layer spacing of 4.39 \angstrom
+%	and 4.38 \angstrom in the sandwiched and parallel displaced configurations respectively.
+%        \item The power spectrums used to calculate the reported layer spacings are given in the 
+%        Supplemental Information.  %BJC: "Power spectrum" an okay description here?
+	% BJC: TODO: Overlay plots of tail and headgroup densities
+        %MRS2: repore more precisely what finding is interesting. What does that difference mean?
+%	\item We see a difference in the spacing in the head group versus tail region
+%	because there is more volume to fill with less densely packed carbon chains in the tail region. 
+	% BJC: vvv Need to get the same information for the tail zdfs.
+%	\item Even though the layer spacing is similar, the sandwiched configuration
+%	exhibits more defined layers with its first peak deviating from the mean 
+%        number density by 61 \%. %BJC: I mention how I do this calculation in the methods. Is it clear that I'm doing that here?
+%MRS2: fine for description for now.          
+%	\item The parallel displaced configuration deviates from the mean by only 
+%	12 \% in comparison.
+%MRS2: is this that unexpected, since parallel displaces should have layers that alternate anyway?
+%BJC: true, but I'm just stating the facts
+%  \end{itemize}
+
+%  \begin{figure}
+%        \centering
+%        \begin{subfigure}{0.45\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf5layered.png}
+%                \caption{}\label{fig:zdf_layered}
+%        \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf5offset.png}
+%                \caption{}\label{fig:zdf_offset}
+%        \end{subfigure}
+%        \caption{Pair distribution functions of aromatic carbons for the
+%        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
+%       parallel displaced configurations. Clear periodic maxima in the
+%        $z$ probability density indicate distinct layers. The magnitude
+%        of the spikes with respect to the average suggest that the 5
+%        monomer per layer, sandwiched configuration possesses a higher
+%        degree of layer partitioning.}\label{fig:zdf}
+%  \end{figure}
+
+  % BJC: Even though I will shift focus to only 5 monomers per layer, I will put other data
+  % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information 
+  %MRS2: good.
+  %\begin{figure}
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{p2p.png}
+%	\caption{The pore spacing (given in nm) of the model increases as
+%	number of monomers in each layer increases. The pore spacing of a system
+%	starting in the sandwiched configuration is systematically lower than 
+%	that started in an offset configuration. Systems built with 5 monomers
+%	per layer in a parallel displaced configuration result in a pore spacing
+%	closest to the experimental 4.12 nm}~\label{fig:p2p}
+ % \end{figure}
 
@@
 
-  We answer question (\ref{point:orientation}) by simulating X-ray diffraction patterns produced from
-  equilibrated MD trajectories.
+%  We answer question (\ref{point:orientation}) by simulating X-ray diffraction patterns produced from
+%  equilibrated MD trajectories.
   %We created systems using three distinct initial configurations and examined
   %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
-  \begin{itemize}
-	\item Systems of 5 monomers per layer in the parallel displaced and sandwiched
-	configurations were tested.
-        \item Simulated patterns were generated using portions of simulation
-        trajectory after equilibration.
-        \item The patterns for both structures are shown and compared to experiment
-	in Figure ~\ref{fig:XRDsim}.
-  \end{itemize}
+%  \begin{itemize}
+%	\item Systems of 5 monomers per layer in the parallel displaced and sandwiched
+%	configurations were tested.
+ %       \item Simulated patterns were generated using portions of simulation
+  %      trajectory after equilibration.
+   %     \item The patterns for both structures are shown and compared to experiment
+	%in Figure ~\ref{fig:XRDsim}.
+%  \end{itemize}
 %
@@
   %BJC: Put this paragraph first since it is the conclusion I want to stick
-  The parallel displaced configuration results in a simulated XRD pattern with
-  the closest match to experiment.
-  \begin{itemize}
-        \item It produces the only pattern that exhibits all major reflections
-        \item R-alkanes, R-pores and R-$\pi$ appear as they do in the sandwiched configuration.
-        \item R-spots appears, however with a lower intensity relative to R-alkanes
-        when compared to the sandwiched configuration.
-        \item R-helix appears apparently due to the parallel displaced aromatic rings
+%  The parallel displaced configuration results in a simulated XRD pattern with
+%  the closest match to experiment.
+%  \begin{itemize}
+%        \item It produces the only pattern that exhibits all major reflections
+%        \item R-alkanes, R-pores and R-$\pi$ appear as they do in the sandwiched configuration.
+%        \item R-spots appears, however with a lower intensity relative to R-alkanes
+%        when compared to the sandwiched configuration.
+%        \item R-helix appears apparently due to the parallel displaced aromatic rings
         %BJC: Maybe a figure to explain why this happens
-  \end{itemize}
+%  \end{itemize}
 
   %BJC: Put this paragraph second so people understand why it is wrong and don't fixate on how nice the spots are
-  Simulated XRD of the sandwiched configuration contains all experimental features
-  except for R-helix.
-  \begin{itemize}
-        \item R-alkanes and R-pores appear in the expected locations.
-        \item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
-        in experiment. The rings prefer to stack $\approx 4.2 \angstrom$ apart as % update distance if needed
-        opposed to 3.7 \angstrom~.
-        \item Most notably, R-spots appears in the expected location, which suggests 
-        that there is something intrinsic to closer packing that gives rise 
-        to such features. 
-  \end{itemize}
+%  Simulated XRD of the sandwiched configuration contains all experimental features
+%  except for R-helix.
+%  \begin{itemize}
+%        \item R-alkanes and R-pores appear in the expected locations.
+%        \item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
+%        in experiment. The rings prefer to stack $\approx 4.2 \angstrom$ apart as % update distance if needed
+%        opposed to 3.7 \angstrom~.
+%        \item Most notably, R-spots appears in the expected location, which suggests 
+%        that there is something intrinsic to closer packing that gives rise 
+%        to such features. 
+%  \end{itemize}
 
@@
 
-  \begin{figure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \vspace{-0.2em}
-        \includegraphics[width=1.018\linewidth]{layered_rzplot.png}
-        \caption{}~\label{fig:rz_layered}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \vspace{0.25em}
-        \includegraphics[scale=0.0987]{WAXS_raw.png}
-        \caption{}~\label{fig:raw_waxs}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{offset_rzplot.png}
-        \caption{}~\label{fig:rz_offset}
-  \end{subfigure}
-  \begin{subfigure}{0.0544\linewidth}
-        \centering
-        \vspace{-3.30em}
-        \includegraphics[width=\linewidth]{colorbar_jet.png}
-  \end{subfigure}
-  \caption{The simulated X-ray diffraction patterns for simulations run in the
-  sandwiched (a) and parallel-displaced (c) configurations are compared to experiment (b). 
-  The parallel displaced configuration is the only one that exhibits all major
-  reflections of interest to some degree}
-  \end{figure}
-
-  R-spots, which appears in both simulated XRD patterns, is a result of the way 
-  alkane tails pack together.
-  \begin{itemize}
-  	\item Previously, the spots in the diffraction pattern had been explained 
-	as the product of tilted alkane chains. % BJC: reference 2014 ACS nano paper
-	\item We measured the tilt angle of the alkane chains and showed that our 
-	system equilibrates to an average tilt angle close to zero degrees ~\ref{fig:tilt} % Could belong in supplemental. Leaving here for now 
-	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
-	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
-        that the spots arise as a consequence of the tails. 
-	\item By removing atoms from the trajectory and simulating a diffraction 
-	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails}).
-	\item Since the tails stay nearly flat, we plotted the centroids of the 
-	tails and measured the angle between each centroid and its nearest neighbors
-	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).  %BJC: at one point Matt mention doing a correlation function instead of just measuring the angles
-	\item We see distinct peaks in the distribution of these angles (Figure~\ref{fig:tail_packing})
-  \end{itemize}
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
-  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
-  indicates an average tilt angle near 7\degree which is far from the 37\degree tilt angle 
-  previously used to explain R-spots}~\label{fig:tilt}
-  \end{figure}
-
-  The peaks in the tilt angle distribution are consistent with the location of R-spots.
-  \begin{itemize}
-	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
-	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
-	of spots are located on the simulated patterns
-	\item We confirmed this conclusion by radially integrating the 2D WAXS pattern for q values
-	between 1.57 and 1.4 (real space between 4 and 4.5 \AA) 
-	\item We observe that distinct peaks appear c.a. 30 $\degree$, in close agreement with the
-	previously measured angle distribution (~\ref{fig:offset_integration}~\ref{fig:layered_integration})
-%	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
-	\item We performed the same integration on the raw experimental data and found the angle
-	at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a 
-	reconcilable difference with our simulated results.  
-  \end{itemize}
-
-  \begin{figure}
-	\centering
-	\begin{subfigure}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
-		\caption{}\label{fig:topdown_tails_only}
-	\end{subfigure}
-	\begin{subfigure}{0.45\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{tails_rzplot.png}
-		\caption{}\label{fig:tails_rzplot}
-	\end{subfigure}
-	\caption{(a) All atoms except carbon atoms making up the tails are removed from the 
-	trajectory. (b) The simulated diffraction pattern of the tail-only trajectory still 
-        shows R-spots}\label{fig:tails}
-        %MRS2: might need to say how the dynamic range is adjusted here with only tails, since otherwise people will be confused with the R-spots being more intense. 
-	%BJC: what do you mean by dynamic range?
-	%BJC: Explain how colorbar is adjusted
-  \end{figure}
-
-  \begin{figure}
-  \centering
-  	\begin{subfigure}{\linewidth}
-	\centering
-		\begin{subfigure}{0.45\textwidth}
-        		\centering
-        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
-        		\caption{}~\label{fig:offset_tails}
-		\end{subfigure}
-		\begin{subfigure}{0.45\textwidth}
-		\centering
-	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
-		        \caption{}~\label{fig:offset_integration}
-		\end{subfigure}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
-	\centering
-		\begin{subfigure}{0.45\textwidth}
-	        \centering
-		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
-		        \caption{}~\label{fig:rz_layered}
-		\end{subfigure}
-		\begin{subfigure}{0.45\textwidth}
-        	\centering
-		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
-		        \caption{}~\label{fig:layered_integration}
-		\end{subfigure}
-	\end{subfigure}
-%MRS: 
-  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
-  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
-  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
-  (b) and (d) respectively.}~\label{fig:tail_packing}
-%MRS2: not clear what the difference is between right and left side figures.
-%BJC: That's good! One is angles measured between tail centroids and the other is radial integration of the simulated xrd patterns. I'll try make that more clear in the caption.
-%MRS3: sorry, I meant to say not clear what the SOURCE of the data is in right vs. left.  Make sure colors and labels are consistent in final 
-%MRS: not clear why some are angles with x axis, and some are angles w neighbors?  Shouldn't it be the same thing plotted in both graphs?
-%BJC: I just need to get the labels right, they are the same thing technically
-  \end{figure}
-
-  The $z$-direction correlation functions show that layers in our model prefer
-  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration
-  with layers stacked 5.0 nm apart and to our surprise, we observed
-  long-term stability of a qualitatively different configuration suggesting
-  that we have found more than one metastable free energy basin, corroborating \ref{point:metastable}.
-  %that the initial distance between layers can influence the approach towards 
-  %equilibrium.
-  \begin{itemize}
-        \item Equilibrated systems built according to the 3.7 \angstrom~layer spacing
-        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore
-        structure.
-        \item We will refer to this large set of configurations, with an open pore, as
-        the ordered pore basin open pore (Figure~\ref{fig:OPbasin}).
-        \item Simulations of systems built with layers stacked 5
-        \angstrom~ apart results in a pore structure characterized by high radial
-        disorder, while still maintaining partitioning between hydrophobic and
-        hydrophilic regions.
- %MRS3: need to address the similar RDFs.
+%  \begin{figure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%        \vspace{-0.2em}
+%        \includegraphics[width=1.018\linewidth]{layered_rzplot.png}
+%        \caption{}~\label{fig:rz_layered}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%        \vspace{0.25em}
+%        \includegraphics[scale=0.0987]{WAXS_raw.png}
+%        \caption{}~\label{fig:raw_waxs}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%        \includegraphics[width=\linewidth]{offset_rzplot.png}
+%        \caption{}~\label{fig:rz_offset}
+%  \end{subfigure}
+%  \begin{subfigure}{0.0544\linewidth}
+%        \centering
+%        \vspace{-3.30em}
+%        \includegraphics[width=\linewidth]{colorbar_jet.png}
+%  \end{subfigure}
+%  \caption{The simulated X-ray diffraction patterns for simulations run in the
+%  sandwiched (a) and parallel-displaced (c) configurations are compared to experiment (b). 
+%  The parallel displaced configuration is the only one that exhibits all major
+%  reflections of interest to some degree}
+%  \end{figure}
+
+%  The $z$-direction correlation functions show that layers in our model prefer
+%  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration
+%  with layers stacked 5.0 nm apart and to our surprise, we observed
+%  long-term stability of a qualitatively different configuration suggesting
+%  that we have found more than one metastable free energy basin, corroborating \ref{point:metastable}.
+%  %that the initial distance between layers can influence the approach towards 
+%  %equilibrium.
+%  \begin{itemize}
+%        \item Equilibrated systems built according to the 3.7 \angstrom~layer spacing
+%        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore
+%        structure.
+%        \item We will refer to this large set of configurations, with an open pore, as
+%        the ordered pore basin open pore (Figure~\ref{fig:OPbasin}).
+%        \item Simulations of systems built with layers stacked 5
+%        \angstrom~ apart results in a pore structure characterized by high radial
+%        disorder, while still maintaining partitioning between hydrophobic and
+%        hydrophilic regions.
+% %MRS3: need to address the similar RDFs.
 What data can show they are different?
@@
 But surprising the same RDFs.
-        \item This will be called the disordered pore basin (Figure~\ref{fig:DPbasin}).
-        \item This LLC membrane may exist in at least two metastable states.
-        \item The distinct difference in pore structure exhibited by each phase will
-        likely lead to different transport mechanisms.
-        \item Because the pore structure will vary between each basin, understanding
-        which phase exists experimentally is necessary in order to ensure we are
-        studying the system which actually dominates.
-  \end{itemize}
-
-  \begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{280K_tramp_close.png}
-                \caption{}\label{fig:OPbasin}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
-                \caption{}\label{fig:DPbasin}
-        \end{subfigure}
-        \caption{From a qualitative standpoint, the ordered pore basin (a) is characterized by a
-        hollow cylindrical pore while pores in the disorder pore basin (b) are characterized by a
-        higher degree of radial disorder}\label{fig:basins}
-%MRS3: see note on RDF.
-  \end{figure}
+%        \item This will be called the disordered pore basin (Figure~\ref{fig:DPbasin}).
+%        \item This LLC membrane may exist in at least two metastable states.
+%        \item The distinct difference in pore structure exhibited by each phase will
+%        likely lead to different transport mechanisms.
+%        \item Because the pore structure will vary between each basin, understanding
+%        which phase exists experimentally is necessary in order to ensure we are
+%        studying the system which actually dominates.
+%  \end{itemize}
+
+%  \begin{figure}[!ht]
+%        \centering
+%        \begin{subfigure}[b]{0.475\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{280K_tramp_close.png}
+%                \caption{}\label{fig:OPbasin}
+%        \end{subfigure}
+%        \begin{subfigure}[b]{0.475\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
+%                \caption{}\label{fig:DPbasin}
+%        \end{subfigure}
+%        \caption{From a qualitative standpoint, the ordered pore basin (a) is characterized by a
+%        hollow cylindrical pore while pores in the disorder pore basin (b) are characterized by a
+%        higher degree of radial disorder}\label{fig:basins}
+%%MRS3: see note on RDF.
+%  \end{figure}
 
   % INSERT XRD of disordered basin
-
-  In order to address \ref{point:poredefinition} and to further understand the structural difference 
-  between the ordered pore and disordered pore basins, we plotted the number of densities of
-  heavy atoms in the head group and tail regions of the monomers in addition to the sodium ions.
-  (See Supplemental Information for definition of head group and tail regions) 
-  \begin{itemize}
-	\item For the hydrophilic region, we used the carbon atoms making up the aromatic ring
-	\item For the hydrophobic components we used all carbon atoms of the monomer tails
-  \end{itemize}
+%
+%  In order to address \ref{point:poredefinition} and to further understand the structural difference 
+%  between the ordered pore and disordered pore basins, we plotted the number of densities of
+%  heavy atoms in the head group and tail regions of the monomers in addition to the sodium ions.
+%  (See Supplemental Information for definition of head group and tail regions) 
+%  \begin{itemize}
+%	\item For the hydrophilic region, we used the carbon atoms making up the aromatic ring
+%	\item For the hydrophobic components we used all carbon atoms of the monomer tails
+%  \end{itemize}
 
@@
   % doesn't this structur have a different pore-to-pore distance.
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.55\textwidth}
-        \includegraphics[width=1\linewidth]{offset_density.png}
-        \caption{}
-        \label{fig:offset_density}
-  \end{subfigure}
-  \begin{subfigure}{0.55\textwidth}
-        \includegraphics[width=1\linewidth]{layered_density.png}
-        \caption{}
-        \label{fig:offset_density}
-  \end{subfigure}
-  \begin{subfigure}{0.55\textwidth}
-        \includegraphics[width=1\linewidth]{disordered_density.png}
-        \caption{}
-        \label{fig:offset_density}
-  \end{subfigure}
-  \caption{(a) Parallel Displaced (b) Sandwiched (c) ``Disordered''}~\label{fig:densities}
-  \end{figure}
-
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.55\textwidth}
+%        \includegraphics[width=1\linewidth]{offset_density.png}
+%        \caption{}
+%        \label{fig:offset_density}
+%  \end{subfigure}
+%  \begin{subfigure}{0.55\textwidth}
+%        \includegraphics[width=1\linewidth]{layered_density.png}
+%        \caption{}
+%        \label{fig:offset_density}
+%  \end{subfigure}
+%  \begin{subfigure}{0.55\textwidth}
+%        \includegraphics[width=1\linewidth]{disordered_density.png}
+%        \caption{}
+%        \label{fig:offset_density}
+%  \end{subfigure}
+%  \caption{(a) Parallel Displaced (b) Sandwiched (c) ``Disordered''}~\label{fig:densities}
+%  \end{figure}
 %MRS3: this needs a caption, and need to write some text analyzing it.
@@
 Very interesting regardless!
+
+  \subsection{Pore composition}
+
+  STOP HERE!!
 

### 2018-04-24 HII/Scripts/fft3d.py

@@ -41,6 +41,9 @@ def initialize():
     parser.add_argument('-traj', help='Name of trajectory file to fourier transform')
     parser.add_argument('-avg', action="store_true", help='Valid when -traj is specified. Average histograms of atomic'
                         'positions over trajectory and then take fourier transform once of averaged array')
+    parser.add_argument('-begin', default=0, type=int, help='Frame to begin calculations at')
+    parser.add_argument('-end', default=-1, type=int, help='Frame to end calculations at')
+
 
     args = parser.parse_args()
 
@@ -293,11 +296,18 @@ def normalize_alkanes(R, Z, Raw_Intensity, inner, outer, angle):
 
     angles = []
     intensity = []
+
+    test = np.zeros_like(Raw_Intensity)
     for i in range(R.shape[0]):
         for j in range(Z.shape[0]):
             if inner < np.linalg.norm([R[i], Z[j]]) < outer:
                 angles.append((180/np.pi)*np.arctan(Z[j]/R[i]))
                 intensity.append(Raw_Intensity[i, j])
+                test[i, j] = Raw_Intensity[i, j]
+
+    # plt.imshow(test.T)
+    # plt.show()
+    # exit()
 
     inds = np.digitize(angles, bins)
 
@@ -381,7 +391,7 @@ if __name__ == "__main__":
             # compute structure factor of structural input
 
             if args.traj:
-                t = md.load(args.traj, top=args.gro)
+                t = md.load(args.traj, top=args.gro)[args.begin:]
             else:
                 t = md.load(args.gro)
 
@@ -569,8 +579,9 @@ if __name__ == "__main__":
 
         if args.gro:
             averaged, rfin, zfin = angle_average(freq_x, freq_y, freq_z, fft, ucell=ucell)
-            alkane_intensity = normalize_alkanes(rfin, zfin[0], averaged, 2.23, 2.25, 120)
-            MAX = 3.1 * alkane_intensity * 100
+            alkane_intensity = normalize_alkanes(rfin, zfin[0], averaged, 2.2, 2.5, 120)
+            averaged /= alkane_intensity
+            MAX = 3.1
             xlim = 2.5
             zlim = 2.5
         else:
@@ -590,10 +601,11 @@ if __name__ == "__main__":
 
         NLEVELS = 200
[…]

### 2018-04-26 Ben_Manuscripts/structure_paper/Outline.tex

@@
   \subsection{Density of monomers around pores}
+  %MRS4: Perhaps instead of talking about ``layers'', we can talk about axial density correlations.
+You can say that for the simulated systems, they appear to stay in highly ordered layers, but that the density correlations are low enough that layering is likely not a clear enough description.
   Our simulations best support a model built with 5 monomers per layer based on
@@
   \begin{itemize}  
+  %MRS4: somewhere you need to talk about the range of systems that were built, as that indicates the range of behaviors that are observed.
   		\item We built systems in both the parallel displaced and sandwiched configurations 			with layers initially spaced 3.7 \AA~apart according to the dry equilibration 
@@
   		\item R-alkanes and R-pores appear in the expected location
+    %MRS4: we will need to provide more details: more intense is just qualiatative.
   		\item R-pores is more intense than experiment, likely because we are simulating a 
@@
 	    which decreases the overall intensity.
+    %MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for the difference in intensity ratio. Some of the experiments should help explain it better. Let's talk!
 	  \item R-$\pi$ appears at a lower $q_z$ value than experiment. In both systems, the
@@
 	    are more disordered than the experimental system at 300K.  
+            %MRS4: are they really missing?  If Fig 7 is 300K, sandwiched seems to have it, and parallel displaced is hard to tell because it's covered by the main pi-pi-stacking
+            %MRS4: interesting that the main pi-pi stacking follows the isotropc alkane curve so significantly.
 	    \item R-helix does not appear in either case.
+            %MRS4: is r-helix a good name, when a helix would appear on either side of the center, not the center itself?
   \end{itemize}
@@
 	\end{subfigure} 
+    %MRS4: caption is probably too long.
     \caption{We hypothesize that R-spots is the result of ordered tail packing.
@@
   		dimers of benzene and substituted benzene.
+%MRS: don't need to include this point.
   		\item Tauer and Sherrill explored the binding energies of tetramers of benzene, but
@@
    tails. 
+  %MRS4: we will need to wait to see the results for this come out to really discuss this well.
    \begin{itemize}

### 2018-04-27 Ben_Manuscripts/structure_paper/Outline.tex
Outline updates

@@
 \newcommand{\angstrom}{\textup{\AA}}
+\newcommand{\colormap}{jet}  % colorbar to use
 \usepackage{cleveref}
@@
         be traced by a helix, then for each turn in the helix, there should be
-        two aromatic rings. For this reason it will be referred to as R-helix.
+        two aromatic rings. For this reason it will be referred to as R-double.
         \item A third major reflection is marked by a low intensity ring located
@@
   %MRS4: somewhere you need to talk about the range of systems that were built, as that indicates the range of behaviors that are observed.
-  		\item We built systems in both the parallel displaced and sandwiched configurations 			with layers initially spaced 3.7 \AA~apart according to the dry equilibration 
-  		procedure.
-  		\item The pore-to-pore spacing is stable in all systems are stable after 400 ns of 
-  		simulation. Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all 
-  		systems tested. 
+  		\item We built systems in both the parallel displaced and sandwiched configurations and
+  		equilibrated them according to the dry equilibration procedure.
+  		\item We test all systems with an initial layer spacing, l, of 3.7 \AA.
+  		\item We tested 4 additional systems with layers initially spaced 5 \AA~apart (See 
+  		supporting info for more details on sensitivity to initial layer spacing)
+  		\item The pore-to-pore spacing is stable in all systems after 400 ns of simulation. 
+  		Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems 
+  		tested. 
   		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
@@
 	    (Figure~\ref{fig:SAXS}).
+	    \item comment about disordered systems
   \end{itemize}
@@
 
+  % BJC4: I will add 6 mon/layer disordered data once I have it.
   \begin{figure}
@@
 	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
-			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
-			 increases as the number of monomers in each layer increases. The pore spacing
-			 of systems starting in the sandwiched configuration are systematically lower
-			 than those started in the parallel displaced configuration.}~\label{fig:p2p}
+			 the experimental value of 4.12 nm, regardless of initial layer spacing, l. The 
+			 equilibrated pore spacing of the model increases as the number of monomers 
+			 in each layer increases. The pore spacing of systems starting in the sandwiched 	
+			 configuration are systematically lower than those started in the parallel 
+			 displaced configuration.}~\label{fig:p2p}
   \end{figure}
@@
 	  	\item We tested systems built with 5 monomers per layer in the parallel 
-		displaced and sandwiched configurations at 300K.
+		displaced and sandwiched configurations at 300 K with layers initially spaced
+		3.7 \AA and 5.0 \AA apart.
 		\item We generated simulated patterns using portions of simulation trajectory
 		after equilibration.
-		\item The patterns for both structures are shown and compared to experiment
+		\item The patterns for all structures are shown and compared to experiment
 		in Figure~\ref{fig:XRDsim}.
@@
 %  Simulated XRD of the sandwiched configuration contains all experimental
-%  features except for R-helix. R-alkanes, R-spots and R-pores appear close to their
+%  features except for R-double. R-alkanes, R-spots and R-pores appear close to their
 %  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
@@
 %  Like the sandwiched configuration, the parallel displaced configuration creates
-%  a simulated XRD pattern with all major experimental reflections except for R-helix.
+%  a simulated XRD pattern with all major experimental reflections except for R-double.
 %  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
 %  and R-$\pi$ appear, however with a lower intensity
-%  relative to R-alkanes when compared to the sandwiched configuration. R-helix
+%  relative to R-alkanes when compared to the sandwiched configuration. R-double
 %  appears due to the parallel displaced aromatic rings. It is a subharmonic of
@@
 
-% BJC3: update with 300K pics. Presented separately from 280K for now. 
-  \begin{figure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \vspace{-0.2em}
-        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_offset_300K.png}
-        \caption{}~\label{fig:rz_offset}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-%        \vspace{0.25em}
-        \includegraphics[scale=0.285]{WAXS_raw.png}
-        \caption{}~\label{fig:raw_waxs}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_layered_300K.png}
-        \caption{}~\label{fig:rz_layered}
-  \end{subfigure}
-  \begin{subfigure}{0.0544\linewidth}
-        \centering
-        \vspace{-4.00em}
-        \includegraphics[width=\linewidth]{colorbar_seismic.png}
-  \end{subfigure}
-%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced.
-Any thoughts why?
-We can discuss in person.
-And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
-%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
-%BJC2: Sure, I'll add that to supporting info
-  \caption{The simulated XRD pattern generated from the equilibrated trajectory
-	  of the parallel displaced configuration (a) exhibits all major reflections
-	  present in the experimental WAXS pattern (b). The simulated XRD pattern
-	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
-	  all major reflections except R-helix.}
-  \label{fig:XRDsim}
+%BJC4: I'm not sure what the best way to set up this figure is yet.
+  \begin{figure}[htb]
+	\centering
+	\begin{subfigure}{0.4\linewidth}
+	\centering
+			\begin{subfigure}{\textwidth}
+		       		\centering
+	        		\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
+	        		\caption{Experimental WAXS}~\label{fig:offset_tails}
+			\end{subfigure}
+	\end{subfigure}
+	\begin{subfigure}{0.28\linewidth}
+			\begin{subfigure}{\textwidth}
+			\centering
+		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet.png}
+			        \caption{Sanwiched}~\label{fig:rzplot_layered_300K}
+			\end{subfigure}
+
+			\begin{subfigure}{\textwidth}
+		       		\centering
+	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet.png}
+	        		\caption{Disordered sandwiched}~\label{fig:rzplot_layered_300K}
+			\end{subfigure}
+	\end{subfigure}
+	\begin{subfigure}{0.28\linewidth}
+	\centering
+			\begin{subfigure}{\textwidth}
+			\centering
+		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet.png}
+			        \caption{Parallel displaced}~\label{fig:rzplot_offset_300K}
+			\end{subfigure}
+
+			\begin{subfigure}{\textwidth}
+			\centering
+		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet.png}
+			        \caption{Disordered parallel displaced}~\label{fig:rzplot_offset_300K_disordered}
+			\end{subfigure}
+	\end{subfigure}
+	\caption{Very descriptive caption}~\label{fig:XRDsim} 
 	\end{figure}
@@
     %MRS4: we will need to provide more details: more intense is just qualiatative.
+    %BJC4: I can include the intensity of the first peak of R-pores in the tables that 
+    % show relative intensities.
   		\item R-pores is more intense than experiment, likely because we are simulating a 
@@
     %MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for the difference in intensity ratio. Some of the experiments should help explain it better. Let's talk!
-	  \item R-$\pi$ appears at a lower $q_z$ value than experiment. In both systems, the
-	    reflection reaches its maximum at c.a. $q_z=1.4$ which means that monomers prefer 
-	    to stack c.a. 4.5 \AA apart rather than 3.7 \AA. This behavior is not surprising since
-	    GAFF models atoms as point charges and does not appropriately model the aromatic
-	    $\pi-\pi$ interactions which would cause the monomers to stack closer together.
-	    \item R-spots is missing in both places, at least visually. The tails in our model
-	    are more disordered than the experimental system at 300K.  
-            %MRS4: are they really missing?  If Fig 7 is 300K, sandwiched seems to have it, and parallel displaced is hard to tell because it's covered by the main pi-pi-stacking
+    %BJC4: So a combo of: domain misalignment, slow dynamics of simulated system, only 4 pores
+    % in unit cell, tortuosity (?)
+    	\item R-spots appears to be weaker in the simulated patterns. They are also partially 
+	    engulfed by the wide R-$\pi$ reflection.
+	    \item We further explore R-spots in Section~\ref{section:rspots}  
+        \item R-$\pi$ appears at a lower $q_z$ value than experiment. In all systems, the
+	    reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers
+	    prefer stack greater than 4.2 \AA apart rather than 3.7 \AA. This behavior is not
+	    surprising since GAFF models atoms as point charges and does not appropriately model 
+	    the aromatic $\pi-\pi$ interactions which would cause the monomers to stack closer
+	    together.
+	    \item We will explore R-$\pi$ in more detail in Section~\ref{section:rpi}.
             %MRS4: interesting that the main pi-pi stacking follows the isotropc alkane curve so significantly.
-	    \item R-helix does not appear in either case.
-            %MRS4: is r-helix a good name, when a helix would appear on either side of the center, not the center itself?
+			%BJC: Might have something to do with the distibution of tilt angles in the tails
+	    \item R-double does not appear in any of the patterns
+	    \item We will explore its possible origins and reasons that it does not appear in our
+	    simulated patterns in Section~\ref{section:rdouble}.
   \end{itemize}
@@
   		\item The reflection does not cross through $q_r = 0 \AA^{-1}$ so it does not
-  		appear for the same reason as R-helix. 
+  		appear for the same reason as R-double. 
+  		\item This type of pattern is characteristic of a helix (reference something)
   		\item It is possible that these reflections contribute to the continuation of
-  		R-helix into R-alkanes, as seen in the experimental pattern. 
-  \end{itemize}
-
-  There are numerical discrepancies between the relative intensities of each reflection when
-  comparing experimental and simulated patterns.
+  		R-double into R-alkanes, as seen in the experimental pattern. 
+  \end{itemize}
+
+  We quantified the numerical discrepancies present when comparing the relative intensities
+  of each reflection of interest between experimental and simulated patterns. 
   \begin{itemize}
   		\item Table~\ref{table:relative_inensities_300K} quantifies the relative intensity
-  		of each reflection.
-  		\item The intensity of R-spots is much lower than experiment (need to update the numbers in that table with 300K results)
-  		\item There is no R-helix intensity
-  		\item R-$\pi$ is nearly an order of magnitude higher in our simulations
-  		compared to experiment.
+  		of each reflection for each system tested.
+  		\item The patterns are normalized so that the average intensity of R-alkanes equals 1. 
+  		% BJC4: I need to explain how I calculated these intensities somewhere. Is this the right
+  		% place to do it? I think it would just be confusing in the methods. I could also move it
+  		% to supplemental.
+  		\item We measured the approximate intensity of R-$\pi$ by measuring the intensity of 
+  		the peak of the cross-section at $q_r=0$. 
+  		\item The relative intensity of R-$\pi$ is significantly higher than experiment in our
+  		simulations.
+  		\item R-spots is measured as the average intensity within the region bounded by a 'spot'.
+  		Spots are identified based on visual inspection. If there is no easily discernable spot,
+  		then the intensity is taken as that of the intersection of R-alkanes at half the $q_z$
+  		value of R-$\pi$, since that is where it appears experimentally. 
+  		\item The intensity of R-spots is slightly lower than experiment in all cases.
+  		\item There is no R-double intensity to be measured.
   \end{itemize}
@@
   \centering
-  \begin{tabular}{cccc}
+  \begin{tabular}{cccccc}
   \toprule
-  		   & \multicolumn{3}{c}{Configuration} \\
+  		   & \multicolumn{5}{c}{Configuration} \\
   \hline
-  Reflection & Experiment & Sandwiched & Parallel Displaced \\
+  Reflection & Experiment & Sandwiched & Parallel Displaced & Disordered Sandwiched & Disordered Parallel Displaced \\
   \midrule
-  R-alkanes & 1.0 &  1.0 &  1.0  \\  
-  R-$\pi$   & 2.8 & 18.0 & 14.0  \\
-  R-spots   & 1.5 &  1.6 &  1.2  \\  % Need to get these actual data points
-  R-helix   & 0.9 &  --  & --    \\ 
+  R-alkanes & 1.0 &  1.0 &  1.0 & 1.0 & 1.0  \\  
+  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
+  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
+  R-double  & 0.9 &  --  & --   &  -- & --   \\ 
   \bottomrule
   \end{tabular}
-  \caption{The relative intensities of reflections of interest}
+  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
+  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
+  than experiment and R-spots reflections that are slightly lower than experiment. R-double
+  does not appear in any patterns, and thus has no measurable intensity.}
   \label{table:relative_inensities_300K} 
@@
 %  The simulated XRD pattern produced from the sandwiched configuration is missing
-%  R-helix and R-spots. 
+%  R-double and R-spots. 
 %  \begin{itemize}
@@
 %  The simulated XRD pattern generated from the parallel displaced configuration is also
-%  missing R-helix and R-spots.
+%  missing R-double and R-spots.
 %  \begin{itemize}
@@
 %  		high intensity. 
-%  		\item R-helix is not present, however off-axis reflections appear at the same value 
-%  		of $q_z$ where we expect to see R-helix. These appear since there is a helical 
+%  		\item R-double is not present, however off-axis reflections appear at the same value 
+%  		of $q_z$ where we expect to see R-double. These appear since there is a helical 
 %  		arrangement of monomers in the parallel displaced configuration. A helix alone will
@@
 
-%  The simulated diffraction patterns indicate that there is something going wrong
-%  with the way the system is modeled. We must address all of these issues and justify
-%  their occurrence.
   There are clear differences between our simulated results and experimental results
   that must be addressed and justified. We will explore the origin of each experimental 
-  reflection and hypothesize why they do not appear in our simulated patterns. Specifically,
-  we want answer:  
-  %BJC: I could number these and answer them individually
+  reflection and form structural hypotheses related to their appearance in our simulated 
+  patterns. Specifically, we want answer:  
   \begin{enumerate}
@@
   	\item Why is the intensity of R-$\pi$ so much greater than experiment?
-  	\item What is the origin of R-helix?
+  	\item What is the origin of R-double?
   \end{enumerate}
 
-  \subsubsection{Origin of R-spots}
-
-  We observed R-spots when we ran simulations of each system at 280K. (figure to be added - include with 300K patterns or keep separate??)
+  \subsubsection{Origin of R-spots}\label{section:rspots}
+
+  We observe an increase in the intensity of R-spots when we simulate systems at 280K. 
   \begin{itemize}
   		\item R-spots is most intense in the sandwiched configuration
-  		\item Still no R-helix
-  \end{itemize}
+  		(Figure~\ref{fig:sandwiched280K}).
+  		\item The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3) 
+  		\item Still no R-double
+  		\item We can use this configuration to more thoroughly explore the origin of R-spots.
+  \end{itemize}
+
+  \begin{figure}
+	  \begin{subfigure}{0.45\linewidth}
+	  	\centering
+	  	\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
+	  	\caption{}
+	  \end{subfigure}
+	  \begin{subfigure}{0.45\linewidth}
+	  	\centering
+	  	\includegraphics[width=\linewidth]{rzplot_layered_280K_jet.png}
+	  	\caption{}\label{fig:sandwiched280K}
+	  \end{subfigure}
+  \caption{R-spots increases in intensity when the temperature of the system is lowered to 280K.
+  In this case, the simulated R-spots is more intense than experiment.}
+  \end{figure}
+
+  % %BJC3: update with 300K pics. Presented separately from 280K for now. 
+%  \begin{figure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%        \vspace{-0.2em}
+%        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_offset_300K.png}
+%        \caption{}~\label{fig:rz_offset}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%        \vspace{0.25em}
+%        \includegraphics[scale=0.285]{WAXS_raw.png}
+%        \caption{}~\label{fig:raw_waxs}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_layered_300K.png}
+%        \caption{}~\label{fig:rz_layered}
+%  \end{subfigure}
+%  \begin{subfigure}{0.0544\linewidth}
+%        \centering
+%        \vspace{-4.00em}
+%        \includegraphics[width=\linewidth]{colorbar_seismic.png}
+%  \end{subfigure}
+%%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced.
+Any thoughts why?
+We can discuss in person.
+And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
+%%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
+%%BJC2: Sure, I'll add that to supporting info
+%%  \caption{The simulated XRD pattern generated from the equilibrated trajectory
+%%	  of the parallel displaced configuration (a) exhibits all major reflections
+%%	  present in the experimental WAXS pattern (b). The simulated XRD pattern
+%%	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
+%%	  all major reflections except R-double.}
+%  \label{fig:XRDsim}
+%  \end{figure}
 
   %BJC: might be able to combine with other table
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{cccc}
-  \toprule
-  		   & \multicolumn{3}{c}{Configuration} \\
-  \hline
-  Reflection & Experiment & Sandwiched & Parallel Displaced \\
-  \midrule
-  R-alkanes & 1.0 &  1.0 &  1.0  \\  
-  R-$\pi$   & 2.8 & 27.0 & 119.0  \\
-  R-spots   & 1.5 &  1.6 &  1.2  \\  
-  R-helix   & 0.9 &  --  & --    \\ 
-  \bottomrule
-  \end{tabular}
-  \caption{The relative intensities of reflections of interest}
-  \label{table:relative_inensities_300K} 
-  \end{table}
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{cccc}
+%  \toprule
+%  		   & \multicolumn{3}{c}{Configuration} \\
+%  \hline
+%  Reflection & Experiment & Sandwiched & Parallel Displaced \\
+%  \midrule
+%  R-alkanes & 1.0 &  1.0 &   1.0  \\  
+%  R-$\pi$   & 2.8 & 27.1 & 119.3  \\
+%  R-spots   & 1.3 &  1.6 &   1.2  \\  
+%  R-double  & 0.9 &  --  &   --   \\ 
+%  \bottomrule
+%  \end{tabular}
+%  \caption{The relative intensities of reflections of interest}
+%  \label{table:relative_inensities_280K} 
+%  \end{table}
 
   %BJC3: following taken from draft.tex
-  The R-spots signal, which appears in both simulated XRD patterns, is not a
-  result of alkane chain tilt. Previous literature has attributed the spots in
-  this particular WAXS pattern as the product of tilted alkane
+  The R-spots signal is not a result of alkane chain tilt. Previous literature
+  has attributed the spots in this particular WAXS pattern as the product of tilted alkane
   chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched
-  configuration since R-spots appears with the most strength in its simulated XRD
-  pattern. We measured the tilt angle of the alkane chains and showed that our
-  system equilibrates to an average tilt angle close to zero degrees
+  configuration simulated at 280K since R-spots appears with the most strength in 
+  its simulated XRD pattern. We measured the tilt angle of the alkane chains and 
+  showed that our system equilibrates to an average tilt angle close to zero degrees
   (Fig.~\ref{fig:tilt}).
+
+   %BJC4: include dashed line at mean. 
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
+  \caption{We measured the angle made between each monomer alkane tail and the
+	  membrane plane. The average tilt angle is near 7\degree~which is far from the
+	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
+  \end{figure}
 
@@
   the tails. By removing all non-tail atoms from the trajectory and simulating a
-  diffraction pattern, we were able to isolate the cause of the spots to the
+  diffraction pattern with the remaining atoms, we were able to isolate the cause of the spots to the
   tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
@@
 
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
-  \caption{We measured the angle made between each monomer alkane tail and the
-	  membrane plane. The average tilt angle is near 7\degree~which is far from the
-	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
-  %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
-  %BJC2: good idea
-  \end{figure}
-
+%  The peaks in the nearest neighbor angle distribution are consistent with the
+%  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
+%  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
+%  location where the highest intensity of spots are located on the simulated
+%  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
+%  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
+%  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
+%  \degree$, in close agreement with the previously measured angle distribution
+%  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
+%  performed the same integration on the raw experimental data and found the angle
+%  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
+%  is a reconcilable difference with our simulated results.
+
+  %BJC: modification of above paragraph to only include 280K sandwiched data
   The peaks in the nearest neighbor angle distribution are consistent with the
@@
 		\centering
-		\includegraphics[width=\textwidth]{tails_rzplot.png}
+		\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
 		\caption{}\label{fig:tails_rzplot}
@@
 
+%  \begin{figure}[!htb]
+%  \centering
+%  	\begin{subfigure}{\linewidth}
+%	\centering
+%		\begin{subfigure}{0.45\textwidth}
+%        		\centering
+%        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
+%        		\caption{}~\label{fig:offset_tails}
+%		\end{subfigure}
+%		\begin{subfigure}{0.45\textwidth}
+%		\centering
+%	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
+%		        \caption{}~\label{fig:offset_integration}
+%		\end{subfigure}
+%	\end{subfigure}
+%	\begin{subfigure}{\linewidth}
+%	\centering
+%		\begin{subfigure}{0.45\textwidth}
+%	        \centering
+%		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
+%		        \caption{}~\label{fig:layered_tails}
+%		\end{subfigure}
+%		\begin{subfigure}{0.45\textwidth}
+%        	\centering
+%		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
+%		        \caption{}~\label{fig:layered_integration}
+%		\end{subfigure}
+%	\end{subfigure} 
+%    %MRS4: caption is probably too long.
+%    \caption{We hypothesize that R-spots is the result of ordered tail packing.
+%	  Defining the membrane plane to be 0\degree, we measured the angles between each
+%	  alkane chain tail centroid and its nearest neighbor centroids for the
+%	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
+%	  that appear in each distribution are centered near $\pm~33\degree$. We radially
+%	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
+%	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
+%	  Peaks appear in the same location as the angle distributions which corroborates
+%	  our hypothesis. Further, we note that the peaks are strongest in both plots
+%	  associated with the sandwiched configuration. As shown in Figure
+%	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
+%	  more intense R-spots reflections. Note that plots of integrated intensity are
+%	  normalized so the average alkane intensity (excluding reflections $\pm
+%	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
+%	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
+%  \end{figure}
+
+  % BJC4: modification of above figure to only included sandwiched data. The rest can go
+  % in supporting info.
   \begin{figure}[!htb]
   \centering
-  	\begin{subfigure}{\linewidth}
-	\centering
-		\begin{subfigure}{0.45\textwidth}
-        		\centering
-        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
-        		\caption{}~\label{fig:offset_tails}
-		\end{subfigure}
-		\begin{subfigure}{0.45\textwidth}
-		\centering
-	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
-		        \caption{}~\label{fig:offset_integration}
-		\end{subfigure}
-	\end{subfigure}
 	\begin{subfigure}{\linewidth}
@@
 	\end{subfigure} 
-    %MRS4: caption is probably too long.
     \caption{We hypothesize that R-spots is the result of ordered tail packing.
@@
 	  alkane chain tail centroid and its nearest neighbor centroids for the
-	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
+	  equilibrated sandwiched configuration simulated at 280K. Peaks
 	  that appear in each distribution are centered near $\pm~33\degree$. We radially
 	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
-	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
+	  configuration within the region bounding R-alkanes.
 	  Peaks appear in the same location as the angle distributions which corroborates
-	  our hypothesis. Further, we note that the peaks are strongest in both plots
-	  associated with the sandwiched configuration. As shown in Figure
-	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
-	  more intense R-spots reflections. Note that plots of integrated intensity are
-	  normalized so the average alkane intensity (excluding reflections $\pm
-	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
-	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
+	  our hypothesis.}~\label{fig:tail_packing}
   \end{figure}
 
-  There are a couple reasons why we see ordered chain packing at 280 K and not at the
+  There are a couple reasons why we see stronger ordered chain packing at 280 K compared to
   experimental conditions of 300 K.
@@
 
-  \subsubsection{Discrepancies between R-$\pi$}
+  \subsubsection{Discrepancies between R-$\pi$}\label{section:rpi}
 
@@
 
+  %BJC4: the correlation functions of disordered systems are confusing me.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
+  \caption{}\label{fig:z_correlation_sandwich}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_offset.png}
+  \caption{}\label{fig:z_correlation_offset}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
+  \caption{}\label{fig:z_correlation_sandwich_disordered}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
+  \caption{}\label{fig:z_correlation_offset_disordered}
+  \end{subfigure}  
+  \caption{}\label{fig:correlation}
+  \end{figure}
+
   The correlation length between stacked monomer head groups shows the best agreement with
-  experiment for systems simulated at 300K.
+  experimental for systems simulated at 300K.
   %BJC3: explanation of correlation length calculation in methods section. 
@@
 
-  \subsubsection{Origin of R-helix}
-
-  R-helix will not show up in any of the models tested so far.
+  \subsubsection{Origin of R-double}\label{section:rdouble}
+
+  R-double will not show up in any of the models tested so far.
   \begin{itemize}
         \item All monomers used to build initial configurations are identical. There is no way 	
-        to produce R-helix without a more complex initial configuration 
+        to produce R-double without a more complex initial configuration 
         \item We calculated the structure factor of simple systems that mimic the parallel
-        displaced and sandwiched configurations. Neither give rise to R-helix.
+        displaced and sandwiched configurations. Neither give rise to R-double.
         (See Figure "fourier transforms of simple systems").
@@
 
-  We can produce R-helix if our initial configuration contains alternating parallel and
+  We can produce R-double if our initial configuration contains alternating parallel and
   antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
@@
 
-  We can also produce R-helix if layers are not uniformly spaced. Rather, monomers might form 
+  We can also produce R-double if layers are not uniformly spaced. Rather, monomers might form 
   pairs that stack less than 3.7 \AA apart, and whose center of masses are spaced 7.4 \AA 
@@
   		restraints are applied to heavy atoms of the phenyl rings.
-  		\item Many \textit{ab initio} studies have measured the equilibrium distance between
-  		dimers of benzene and substituted benzene.
-%MRS: don't need to include this point.
-  		\item Tauer and Sherrill explored the binding energies of tetramers of benzene, but
-  		did not explore the report the equilibrium distance between benzene rings. 
-  		\item Even if there have been other studies of the equilibrium distance between 
-  		stacks of benzene rings, it still does not model our system which has many 
-  		electron-withdrawing groups and bulky substituents that would likely affect stacking
-  		preferences. 
-  \end{itemize}
-
-  Our final hypothesized configuration which produces R-helix focus on the orientation of the
+%  		\item Many \textit{ab initio} studies have measured the equilibrium distance between
+%  		dimers of benzene and substituted benzene.
+%%MRS: don't need to include this point.
+%  		\item Tauer and Sherrill explored the binding energies of tetramers of benzene, but
+%  		did not explore the report the equilibrium distance between benzene rings. 
+%  		\item Even if there have been other studies of the equilibrium distance between 
+%  		stacks of benzene rings, it still does not model our system which has many 
+%  		electron-withdrawing groups and bulky substituents that would likely affect stacking
+%  		preferences. 
+  \end{itemize}
+
+   Our final hypothesized configuration which produces R-double focus on the orientation of the
    tails. 
-  %MRS4: we will need to wait to see the results for this come out to really discuss this well.
    \begin{itemize}
@@
   		\item This configuration is stable short-term while unrestrained.
-  		\item This may be the most reasonable explanation for the appearance of R-helix. The
+  		\item This may be the most reasonable explanation for the appearance of R-double. The
   		long-term stability of a configuration similar to this may be feasible if monomers
@@
   %	\item The sandwiched configuration shows R-spots in the expected location.
-  %	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
+  %	\item A faint reflection is present in the location of R-double %BJC: but it fades upon further simulation.
   %	\item The parallel displaced configuration contains two lines of high 
@@
   %	chain region due to constructive interference between the two features.
-  %	\item The lines are located where one would expect to see R-helix and, 
+  %	\item The lines are located where one would expect to see R-double and, 
   %	perhaps coincidentally, the intersection with R-alkanes occurs where one 
@@
   %	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
-  %	where R-helix exists.
+  %	where R-double exists.
   %\end{itemize}
@@
   %	but it is difficult to distinguish because of its intersection with the solid
-  %	R-helix line. 
+  %	R-double line. 
         %MRS: Longer simulations are necessary to determine which structure
@@
 %  \begin{itemize}
-%        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
+%        \item The disordered pore structure exhibits R-alkanes and R-pores but R-double,
 %	R-$\pi$ and R-spots are not present. 
@@
 %        when compared to the sandwiched configuration.
-%        \item R-helix appears apparently due to the parallel displaced aromatic rings
+%        \item R-double appears apparently due to the parallel displaced aromatic rings
         %BJC: Maybe a figure to explain why this happens
@@
 %  Simulated XRD of the sandwiched configuration contains all experimental features
-%  except for R-helix.
+%  except for R-double.
 %  \begin{itemize}
@@
 %	\end{subfigure}
-%	\caption{(a) All major features except R-helix are present in
+%	\caption{(a) All major features except R-double are present in
 %	XRD patterns resulting from an equilibrated sandwiched configuration 
-%	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
+%	in Basin A. R-$\pi$ intersescts R-alkanes. R-double faded during equilbration.
 %	(b) All major features execpt R-spots are present in XRD patterns 
 %	resulting from an equilibrated parallel displaced configuration in Basin A.
-%	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
+%	R-double exists faintly in the expected location. (c) R-pores and R-alkanes
 %	are the only major features present in XRD patterns resulting from an 
@@
 %  configuration gives rise to all reflections of interest. (c) The sandwiched configurations gives rise to a
-%  pattern with all major reflections except R-helix. R-spots is strong relative to R-alkanes in comparison
+%  pattern with all major reflections except R-double. R-spots is strong relative to R-alkanes in comparison
 %  to the parallel displaced configuration. (d) The disordered pore configuration creates a pattern with only
@@
 
-  STOP HERE!!
-
-  We answer (\ref{point:water}) and further support (\ref{point:orientation}) by preparing parallel displaced and
-  sandwiched configurations according to the wet equilibration procedure.
-  \begin{itemize}
-	\item We do not have an experimental measurement of water in the pores
-	\item We tested a range of water concentrations from 0.5 to 5 percent % working on a 0.5 wt % sytstem now just to see
-	\item Our lower bound represents a system with on average 2 water 
-	molecules for each monomer layer.
-	\item Figure ~\ref{fig:solvation} shows results for each configuration.
-%	\item Initially, we decided the number of waters to put in each pore by
-%	estimating the number of hydrogen bonds in which pore entities could participate.
-%	\item In solution, each headgroup has a charge of -1
-%	\item We estimate there to be at least 2 water molecules per layer based 
-%	on various packing configurations and geometric constraints
-%	\item 4 water molecules per layer translates to about 1.6 wt \%
+  We plotted the number densities of heavy atoms in the head group, carbon atoms in the tail
+  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
+  region, we used the carbon atoms making up the aromatic ring. For the tail
+  region we used only carbon atoms of the monomer tails (See Supporting
+  Information for diagram). We average the histograms over at least 50 ns of
+  equilibrated trajectory.
+
+  In all cases, the space in the pore region is filled with sodium ions and
+  head groups. Systems in the ordered pore basin are less dense in
+  the center of the pore. In both the sandwiched and parallel displaced
+  configurations, we see the density of head groups and sodium ions fall to less
+  than 50\% of its maximum at r = 0 (Fig.~\ref{fig:layered_density}). The
+  situation is most pronounced in the sandwiched configuration where the maximum
+  head group density occurs 0.44 nm from the pore center. The parallel displaced
+  configuration reaches its maximum 0.35 nm from the pore center. In contrast,
+  both disordered pore systems show very little difference in density from its
+  maximum. This implies a more uniform distribution of head groups within the
+  pore center. This is the same conclusion drawn from the plots of $g(x,y)$ 
+  (Figure~\ref{fig:xy_correlation}). 
+  % High vacancy is less likely to be stable in the real system
+
+  There is a partition between the hydrophobic and hydrophilic regions, however
+  it is a gradient in composition, rather than an abrupt division. The system
+  does not confine sodium ions and head groups to just within the pore region.
+  Assuming a pore radius of 0.6 nm, we see in all cases, that 19\% of sodium ions
+  exist outside the pore region (except sandwiched, ordered pore, where 16\%
+  are outside the pore). Additionally, we see that in all cases, about 3\% of the
+  plotted tail density is located within the pore region (except sandwiched,
+  ordered pore, where 1.5\% are within the pore region). These observations bring
+  into question how one should define a pore in these types of systems. One
+  usually measures a membrane's pore radius based on the size of a molecule it
+  can reject, however it is not clear where the edges of the pores are and what
+  size molecule would fit through. We leave these investigations for a future
+  study.
+
+  In general, the composition of the pores is similar between all systems. 
+  \begin{itemize}
+  	\item We believe we can study transport in any of the systems presented here and
+  	still extract valuable information.
+  	\item We will need to verify that this assumption is true.
   \end{itemize}
@@
   \centering
-	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
-        %MRS2: include 0% as well? Maybe leave off 5% if not relevant in the end?
-	\label{fig:solvation}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{offset_density.png}
+        \caption{Parallel Displaced, Ordered Pore Basin}
+        \label{fig:offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{layered_density.png}
+        \caption{Sandwiched, Ordered Pore Basin}
+        \label{fig:layered_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
+        \caption{Parallel Displaced, Disorderd Pore Basin}
+        \label{fig:disordered_offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{disordered_density.png}
+        \caption{Sandwiched, Disordered Pore Basin}
+        \label{fig:disorder_layered_density}
+  \end{subfigure}
+  \caption{In all cases, the component radial distribution functions exhibit a
+	  composition gradient transitioning from the hydrophilic to the hydrophobic
+	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
+	  displaced (a), and sandwiched (b) configurations both show the highest
+	  concentrations of ions and head groups away from the pore center. Systems with
+	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
+	  concentrations of ions and head groups near the pore center, implying a more
+	  uniform, disordered pore.}~\label{fig:densities}
   \end{figure}
 
-  In all cases, water disrupts structuring of the model.
-  \begin{itemize}
-	\item The plots in Figure ~\ref{fig:solvation} are normalized 
-	to have the same colorbar as the dry systems. 
-	\item The intensity of the reflections decrease when water is 
-	added to the system.
-	\item In systems built with 5 weight percent water, R-$\pi$ and
-	R-spots become nearly indistinguishable from R-alkanes.
-  \end{itemize}
+  END
+
+%  We answer (\ref{point:water}) and further support (\ref{point:orientation}) by preparing parallel displaced and
+%  sandwiched configurations according to the wet equilibration procedure.
+%  \begin{itemize}
+%	\item We do not have an experimental measurement of water in the pores
+%	\item We tested a range of water concentrations from 0.5 to 5 percent % working on a 0.5 wt % sytstem now just to see
+%	\item Our lower bound represents a system with on average 2 water 
+%	molecules for each monomer layer.
+%	\item Figure ~\ref{fig:solvation} shows results for each configuration.
+%%	\item Initially, we decided the number of waters to put in each pore by
+%%	estimating the number of hydrogen bonds in which pore entities could participate.
+%%	\item In solution, each headgroup has a charge of -1
+%%	\item We estimate there to be at least 2 water molecules per layer based 
+%%	on various packing configurations and geometric constraints
+%%	\item 4 water molecules per layer translates to about 1.6 wt \%
+%  \end{itemize}
+%
+%  \begin{figure}
+%	\centering
+%	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
+%        %MRS2: include 0% as well? Maybe leave off 5% if not relevant in the end?
+%	\label{fig:solvation}
+%  \end{figure}
+%
+%  In all cases, water disrupts structuring of the model.
+%  \begin{itemize}
+%	\item The plots in Figure ~\ref{fig:solvation} are normalized 
+%	to have the same colorbar as the dry systems. 
+%	\item The intensity of the reflections decrease when water is 
+%	added to the system.
+%	\item In systems built with 5 weight percent water, R-$\pi$ and
+%	R-spots become nearly indistinguishable from R-alkanes.
+%  \end{itemize}
 
@@
 %MRS3: we didn't really test if water is  needed to obtain the structures; clearly, w/o water it's metastable for a long time.  We don't need the water simulations to prove this.  
-  Water is not needed to obtain and simulate the correct equilibrium 
-  membrane structure.
-  \begin{itemize}
-	\item We note that water absorbed during membrane synthesis may
-        be present in far lower concentrations than those 
-        tested here.
-	\item We do not eliminate the possibility that water is necessary
-        in order to drive self-assembly. Studying the mechanisms of self assembly is
-	beyond the scope of this work.
-	\item However, once the system has formed the Col\textsubscript{h} 
-	phase, adding water only drives disorder in the structure
-	\item In the equilibrium configuration, if water exists, it is confined
-	to the pore region where there is no driving force for aggregation of 
-	water molecules. 
-	\item In the case of trace water, water molecules will be too sparse to
-	form a hydrogen bonding network.
-  \end{itemize}
+%  Water is not needed to obtain and simulate the correct equilibrium 
+%  membrane structure.
+%  \begin{itemize}
+%	\item We note that water absorbed during membrane synthesis may
+%        be present in far lower concentrations than those 
+%        tested here.
+%	\item We do not eliminate the possibility that water is necessary
+%        in order to drive self-assembly. Studying the mechanisms of self assembly is
+%	beyond the scope of this work.
+%	\item However, once the system has formed the Col\textsubscript{h} 
+%	phase, adding water only drives disorder in the structure
+%	\item In the equilibrium configuration, if water exists, it is confined
+%	to the pore region where there is no driving force for aggregation of 
+%	water molecules. 
+%	\item In the case of trace water, water molecules will be too sparse to
+%	form a hydrogen bonding network.
+%  \end{itemize}
 

### 2018-04-27 HII/Scripts/WAXS.py

@@ -173,43 +173,100 @@ Y = np.linspace(-qmax, qmax, waxs.shape[1])
 # # exit()
 ########################### END Inverse FT ###################################
 
-inner = 1.1
-outer = 1.6
-
-angle = 120
-nbins = 45
-bins = np.linspace(-90, 90, nbins)
-
-bw = 180 / (nbins - 1)
-
-angles = []
-intensity = []
-for i in range(waxs.shape[0]):
-    for j in range(waxs.shape[1]):
-        if inner < np.linalg.norm([X[i], Y[j]]) < outer:
-            angles.append((180/np.pi)*np.arctan(Y[j]/X[i]))
-            intensity.append(waxs[i, j])
-
-inds = np.digitize(angles, bins)
-
-I = np.zeros([nbins])
-counts = np.zeros([nbins])
-for i in range(len(inds)):
-    I[inds[i] - 1] += intensity[i]
-    counts[inds[i] - 1] += 1
-
-#Get average intensity in ring excluding 60 degree slice around top and bottom #######
-
-bin_range = 180 / nbins  # degrees which a single bin covers
-
-start = int((angle/2) / bin_range)  # start at the bin which covers -60 degrees and above
-end = nbins - start  # because of symmetry
-
-total_intensity = np.sum(I[start:end])
-
-avg_intensity = total_intensity / np.sum(counts[start:end])
+# inner = 1.1
+# outer = 1.6
+#
+# angle = 120
+# nbins = 45
+# bins = np.linspace(-90, 90, nbins)
+#
+# bw = 180 / (nbins - 1)
+#
+# angles = []
+# intensity = []
+# for i in range(waxs.shape[0]):
+#     for j in range(waxs.shape[1]):
+#         if inner < np.linalg.norm([X[i], Y[j]]) < outer:
+#             angles.append((180/np.pi)*np.arctan(Y[j]/X[i]))
+#             intensity.append(waxs[i, j])
+#
+# inds = np.digitize(angles, bins)
+#
+# I = np.zeros([nbins])
+# counts = np.zeros([nbins])
+# for i in range(len(inds)):
+#     I[inds[i] - 1] += intensity[i]
+#     counts[inds[i] - 1] += 1
+#
+# #Get average intensity in ring excluding 60 degree slice around top and bottom #######
+#
+# bin_range = 180 / nbins  # degrees which a single bin covers
+#
[…]

### 2018-04-30 Ben_Manuscripts/structure_paper/Outline.tex
Outline updates and new figures

@@
 
-  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
-  into stacked layers which form columnar pores. 
+%  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
+%  into stacked layers which form columnar pores. 
 %BJC: commenting out :There has been no definitive answer in literature regarding the number of monomers in each layer. 
@@
 Maybe just take out that sentence above.
-We want to know 
+%We want to know 
+%\begin{enumerate}
+%\item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}
+%  \begin{itemize}
+%    \item A simple molecular simulation study of a similar molecule suggested
+%    that there are 4 monomers in each layer. Their estimation is based on a
+%    simulated system containing only 16 total monomers which likely does not sufficiently
+%    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
+%    \item A separate calculation based on the volume of the liquid crystal monomers proposes
+%    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
+%    \item A molecular model orders of magnitude larger than any other reported atomistic 
+%    liquid crystal membrane simulations has the best chance of directly answering this question.
+%    \item We can directly change the layer composition and note its effect on membrane structure.
+%  \end{itemize}
+%
+% \item Does our model support the existence of layers and if so, how well defined
+%  are the layers? \label{point:layers}
+%  \begin{itemize}
+%       \item Experimentally, their existence is supported by evidence of strong 
+%       $\pi$-$\pi$ stacking interactions in the direction perpendicular to the
+%       membrane plane.
+%       \item $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups which
+%       leaves no description of what is happening in the monomer tail region
+%       \item The tails may entangle isotropically while stacking order is maintained
+%       among headgroups. 
+%  \end{itemize}  
+%  
+%   \item How do monomers in each layer position themselves with respect to surrounding 
+%   layers? \label{point:orientation}
+%%     Even if we knew the number of monomers in each layer, we still would not know how 
+%%     monomers in each layer are positioned with respect to other layers. 
+%   \begin{itemize}
+%      \item The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly 
+%      in this system\cite{gazit_possible_2002} %is thought to be $\pi$-$\pi$ stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
+%      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
+%      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
+%      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
+%      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
+%      attraction which favors the parallel displaced configuration in all cases
+%      except where the substitutions are extremely electron withdrawing
+%      \cite{waller_hybrid_2006,ringer_effect_2006}.
+%      \item We can use simulated X-ray diffration patterns to compare the two 
+%      stacking configurations. 
+%   \end{itemize}
+%
+%  \item Can the system exist in other metastable states or phases that are not
+%  accessed during experiments? \label{point:metastable}
+%  There remains the possibility that there is more than one metastable state 
+%  associated with a given LLC system.
+%  \begin{itemize}
+%    \item Simulating a membrane atomistically will require many atoms which further
+%    limits the timescales acessible with MD
+%    \item It is reasonable to expect that we will generate configurations which 
+%    are kinetically trapped in a metastable free energy basin
+%    \item We must be able to identify which state is produced experimentally and 
+%    why others are not.
+%  \end{itemize}
+%
+%  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
+%  \begin{itemize}
+%	\item The limited picture that experiment provides tells us that there are
+%        hexagonally packed, hydrophilic regions where transport is likely to occur
+%	\item One may instinctively assume that these regions are tube-like pathways
+%	\item We will explore the composition of the pores and the partition
+%	between the hydrophilic and hydrophobic regions. 
+%  \end{itemize}
+%
+%  \item Is it necessary to include any water in order to appropriately model the 
+%  Col\textsubscript{h} phase? \label{point:water}
+%  \begin{itemize}
+%	\item While the Col\textsubscript{h} phase is described as dry, it is 
+%          %MRS3: ``possible'' -> likely, and give some explanations why we think likely? 
+%	likely that small amounts of ambient water may be leached into the system.
+%	\item The hydrogen bonding network formed by the water may play a role 
+%        in structuring the pore.
+%	\item We can use simulated X-ray diffraction patterns to see if there is
+%        any meaningful structural difference between a "dry" and "wet" system
+%  \end{itemize}
+%  \end{enumerate}
+%  
+  %Once we have addressed all of the above questions, we must show that the 
+  %developed molecular model is consistent with physical observations so that we
+  %can rely on conclusions drawn about structural features characteristic of 
+  %the system.
+
+  %BJC4: Consolidation of points into 4 main questions to answer
+  There are a number of structural questions we wish to answer in this article. We
+  want to know:
   \begin{enumerate}
-\item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}
-  \begin{itemize}
+    \item What is the density of monomers that pack around each hydrophilic core? 
+    \label{point:monomernum}
+ 	\begin{itemize}
+ 		\item Authors often describe this and similar systems as being made up of layers.
  		\item A simple molecular simulation study of a similar molecule suggested
@@
 	    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
-    \item A molecular model orders of magnitude larger than any other reported atomistic 
-    liquid crystal membrane simulations has the best chance of directly answering this question.
-    \item We can directly change the layer composition and note its effect on membrane structure.
-  \end{itemize}
-
- \item Does our model support the existence of layers and if so, how well defined
-  are the layers? \label{point:layers}
-  \begin{itemize}
-       \item Experimentally, their existence is supported by evidence of strong 
-       $\pi$-$\pi$ stacking interactions in the direction perpendicular to the
-       membrane plane.
-       \item $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups which
-       leaves no description of what is happening in the monomer tail region
-       \item The tails may entangle isotropically while stacking order is maintained
-       among headgroups. 
-  \end{itemize}
-
-   \item How do monomers in each layer position themselves with respect to surrounding 
-   layers? \label{point:orientation}
-%     Even if we knew the number of monomers in each layer, we still would not know how 
-%     monomers in each layer are positioned with respect to other layers. 
-   \begin{itemize}
-      \item The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly 
-      in this system\cite{gazit_possible_2002} %is thought to be $\pi$-$\pi$ stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
-      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
-      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
-      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
-      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
-      attraction which favors the parallel displaced configuration in all cases
-      except where the substitutions are extremely electron withdrawing
-      \cite{waller_hybrid_2006,ringer_effect_2006}.
-      \item We can use simulated X-ray diffration patterns to compare the two 
-      stacking configurations. 
-   \end{itemize}
-
-  \item Can the system exist in other metastable states or phases that are not
-  accessed during experiments? \label{point:metastable}
-  There remains the possibility that there is more than one metastable state 
-  associated with a given LLC system.
-  \begin{itemize}
-    \item Simulating a membrane atomistically will require many atoms which further
-    limits the timescales acessible with MD
-    \item It is reasonable to expect that we will generate configurations which 
-    are kinetically trapped in a metastable free energy basin
-    \item We must be able to identify which state is produced experimentally and 
-    why others are not.
-  \end{itemize}
-
-  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
+ 		\item We are careful to avoid the term 'layers' since a liquid crystalline system has,
+ 		by definition, long range order in 1 or 2 spatial dimensions and short range order in 	
+ 		the other dimensions.~\cite{chaikin_principles_1995}  % page 58
+ 		\item In the system we are studying, there are long-range 2D correlations in the 
+ 		hexagonal array of pores and short range correlations in the z-direction.
+		\item We will use our atomistic molecular model to study how the system's structure is
+		effected by the density of monomers surrounding each pore's hydrophilic core. 
+	\end{itemize}
+	\item What structural motif best matches experimental 2D WAXS patterns?\label{point:xrdmatch}
+	\begin{itemize}
+		\item On the short timescales accessible to MD, we observe distinct metastable 
+		configurations which are dependent on starting configuration.
+		\item We simulate XRD patterns of our system and compare them to experimental 2D WAXS 
+		patterns so that we ensure our model creates a nanoscopic chemical environment maximally
+		consistent with experiment within the constraints of our forcefield.
+		\item We are able to confirm and refute previous interpretations of the WAXS pattern.  
+	\end{itemize}
+	\item What is the chemical composition of the pores?\label{point:composition}
 	\begin{itemize}
@@
         hexagonally packed, hydrophilic regions where transport is likely to occur
-	\item One may instinctively assume that these regions are tube-like pathways
-	\item We will explore the composition of the pores and the partition
-	between the hydrophilic and hydrophobic regions. 
-  \end{itemize}
-
+		\item One may instinctively assume that these regions are tube-like pathways with 
+		well-defined boundaries.
+		\item We will explore the composition of the pores, the partition
+		between the hydrophilic and hydrophobic regions, and its sensitivity to initial
+		configuration. 
+	\end{itemize}
     \item Is it necessary to include any water in order to appropriately model the 
@@
     \begin{itemize}
-	\item While the Col\textsubscript{h} phase is described as dry, it is 
-          %MRS3: ``possible'' -> likely, and give some explanations why we think likely? 
-	likely that small amounts of ambient water may be leached into the system.
-	\item The hydrogen bonding network formed by the water may play a role 
-        in structuring the pore.
-	\item We can use simulated X-ray diffraction patterns to see if there is
-        any meaningful structural difference between a "dry" and "wet" system
+		\item While the Col\textsubscript{h} phase is described as dry, it is likely that small 
+		amounts of ambient water may be leached into the system.
+		\item The hydrogen bonding network formed by the water may play a role in structuring the
+		pore.
+		\item We can use simulated X-ray diffraction patterns to see if there is any meaningful 
+		structural difference between a "dry" and "wet" system
     \end{itemize}
   \end{enumerate}
-
-  %Once we have addressed all of the above questions, we must show that the 
-  %developed molecular model is consistent with physical observations so that we
-  %can rely on conclusions drawn about structural features characteristic of 
-  %the system.
 
@@
 
-  %BJC3: Feel free to suggest different words
   \subsection{Density of monomers around pores}
@@
 You can say that for the simulated systems, they appear to stay in highly ordered layers, but that the density correlations are low enough that layering is likely not a clear enough description.
+  %BJC4: Can I support this by plotting the density of head groups axially and show that the peaks are wide/noisy?
   Our simulations best support a model built with 5 monomers per layer based on
@@
   \begin{itemize}  
-  %MRS4: somewhere you need to talk about the range of systems that were built, as that indicates the range of behaviors that are observed.
   		\item We built systems in both the parallel displaced and sandwiched configurations and
@@
 
-  % BJC4: I will add 6 mon/layer disordered data once I have it.
+  % BJC4: I will add 6 mon/layer disordered data once I have it. The 6 mon/layer I have was
+  % equilibrated differently (layers initially spaced 10 \AA apart and jumped straight into
+  % npt), and only for sandwiched config. I have parallel displaced and sandwiched 6mon/layer
+  % running currently.
   \begin{figure}
@@
 		displaced and sandwiched configurations at 300 K with layers initially spaced
-		3.7 \AA and 5.0 \AA apart.
+		3.7 \AA~and 5.0 \AA~apart.
 		\item We generated simulated patterns using portions of simulation trajectory
@@
 		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet.png}
-			        \caption{Sanwiched}~\label{fig:rzplot_layered_300K}
+			        \caption{Sandwiched}~\label{fig:rzplot_layered_300K}
 			\end{subfigure}
@@
     %MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for the difference in intensity ratio. Some of the experiments should help explain it better. Let's talk!
-    %BJC4: So a combo of: domain misalignment, slow dynamics of simulated system, only 4 pores
-    % in unit cell, tortuosity (?)
+    %BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
+    %pores in unit cell, tortuosity (?)
     	\item R-spots appears to be weaker in the simulated patterns. They are also partially 
@@
 	    reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers
-	    prefer stack greater than 4.2 \AA apart rather than 3.7 \AA. This behavior is not
+	    prefer stack greater than 4.2 \AA~apart rather than 3.7 \AA. This behavior is not
 	    surprising since GAFF models atoms as point charges and does not appropriately model 
@@
             %MRS4: interesting that the main pi-pi stacking follows the isotropc alkane curve so significantly.
-			%BJC: Might have something to do with the distibution of tilt angles in the tails
+			%BJC4: Might have something to do with the distibution of tilt angles in the tails
 	    \item R-double does not appear in any of the patterns
@@
   \begin{itemize}
-  		\item There are horizontal reflections at $|q_z|= 0.7 \AA^{-1}$, exactly half of 
+  		\item There are horizontal reflections at $|q_z|= 0.7~\AA^{-1}$, exactly half of 
   		the $q_z$ value of R-$\pi$. 
-  		\item The reflection does not cross through $q_r = 0 \AA^{-1}$ so it does not
+  		\item The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not
   		appear for the same reason as R-double. 
@@
 
+  %BJC4: This paragraph might fit better before qualitative description
   We quantified the numerical discrepancies present when comparing the relative intensities
@@
   		\item Still no R-double
+  		%BJC4: I think the following is a reasonable thing to do. Use a configuration that really
+  		% exhibits R-spots so we can definitively (as best as possible anyways) prove its origin. 
+  		% Otherwise, we will have to go off the 300K data which isn't as clear cut. 
   		\item We can use this configuration to more thoroughly explore the origin of R-spots.
@@
   \caption{We measured the angle made between each monomer alkane tail and the
-	  membrane plane. The average tilt angle is near 7\degree~which is far from the
-	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
+	  membrane plane. The average tilt angle (dashed line) is near -2\degree~which is far from 
+	  the 37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
   \end{figure}
@@
   the tails. By removing all non-tail atoms from the trajectory and simulating a
-  diffraction pattern with the remaining atoms, we were able to isolate the cause of the spots to the
-  tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
+  diffraction pattern with the remaining atoms, we were able to isolate the cause of 
+  the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
   the centroids of the tails and measured the angle between each centroid and its
@@
   The peaks in the nearest neighbor angle distribution are consistent with the
-  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
-  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
+  location of R-spots. The peaks of interest in Figure \ref{fig:layered_tails} 
+  are located at $\pm 33 \degree$ which is the same
   location where the highest intensity of spots are located on the simulated
@@
   pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
-  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
+  and 4.5 \AA~in real space). We observe that distinct peaks appear c.a. $30
   \degree$, in close agreement with the previously measured angle distribution
-  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
+  (Figure~\ref{fig:layered_integration}). We
   performed the same integration on the raw experimental data and found the angle
@@
   experimental conditions of 300 K.
-  \begin{itemize}
-  		\item (1) The difference between 280K and 300K is small. Our forcefield parameters
+  \begin{enumerate}
+  		\item The difference between 280K and 300K is small. Our forcefield parameters
   		may not correctly model the behavior of the tails at 300K (citation?).
-  		\item (2) Monomers aren't as confined at 300 K in our simulations versus experiment.
+  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
   		If the head groups packed 3.7 \AA apart, the tails would be more confined and forced
@@
   		entropically favored disordered state. 
-  \end{itemize}
+  \end{enumerate}
 
@@
   We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
-  of mass of monomer phenyl rings (Figure reference).
+  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}).
   \begin{itemize}
@@
   %BJC4: the correlation functions of disordered systems are confusing me.
-
   \begin{figure}
@@
   \centering
+  %BJC4: This is noisier than l=3.7 angstrom, but I can still pick out peaks. I'm unsure
+  % how to quantify the difference. The correlation length is very similar to the more
+  % ordered configuration.
   \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
@@
   \centering
+  %BJC4: There really aren't any good peaks here. 
   \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
@@
 
+%  The correlation length between stacked monomer head groups shows the best agreement with
+%  experimental for systems simulated in the ordered basin.
+%  %BJC3: explanation of correlation length calculation in methods section. 
+%  \begin{itemize}
+%  		\item Correlation length was calculated by fitting a decaying exponential function
+%  		to all peaks of $g(z)$ for the sandwiched configuration and to every other peak of
+%  		$g(z)$ for the parallel displaced configuration. 
+%%  		\item The correlation length of systems simulated at 280K were 27.7 \AA and 25.2 \AA
+%%  		for the parallel displaced and sandwiched configurations respectively. 
+%  		\item The correlation length of systems simulated in the ordered basin were 11.2 \AA and 
+%  		14.9 \AA  		for the parallel displaced and sandwiched configurations respectively. 
+%  		\item Systems simulated at 300K show correlation closest to the experimental 
+%  		correlation length of 10.1 \AA. They are still slightly more correlated than 
+%  		experiment which would lead to an increase in constructive X-ray scattering. 
+%  \end{itemize}
+
   The correlation length between stacked monomer head groups shows the best agreement with
-  experimental for systems simulated at 300K.
-  %BJC3: explanation of correlation length calculation in methods section. 
+  experimental for systems simulated in the ordered basin.
+  %BJC4: explanation of correlation function calculation in methods section. 
   \begin{itemize}
@@
   		$g(z)$ for the parallel displaced configuration. 
-  		\item The correlation length of systems simulated at 280K were 27.7 \AA and 25.2 \AA
-  		for the parallel displaced and sandwiched configurations respectively. 
-  		\item The correlation length of systems simulated at 300K were 11.2 \AA and 14.9 \AA
-  		for the parallel displaced and sandwiched configurations respectively. 
-  		\item Systems simulated at 300K show correlation closest to the experimental 
+  		\item The correlation length of systems simulated in the ordered basin were 11.2 \AA and 
+  		14.9 \AA  		for the parallel displaced and sandwiched configurations respectively. 
+  		\item Something about disordered systems.
+  		\item Systems simulated in the ordered basin show correlation closest to the experimental 
   		correlation length of 10.1 \AA. They are still slightly more correlated than 
@@
   		\item Nearly all of the intensity in R-$\pi$ of our simulated patterns is concentrated
-  		at a single point. Figure Something shows the same simulated patterns with the upper 
-  		boundary on the colorbar adjusted to be 10x higher. The only visible reflections are
-  		those of R-$\pi$.
+  		at a single point. Figure ~\ref{fig:intense_rpi} shows the same simulated patterns with
+  		the upper boundary on the colorbar adjusted to be 6x higher. The only distinguishable 
+  		reflections are	those of R-$\pi$ and R-pores.
   		\item In the experimental pattern, the intensity is more evenly spread out over all
@@
   \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{sandwich_rzplot_highlimit_cbar.png}
+  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections. Here, the 
+  colorbar was scaled so that the max is 6x higher than all other plots.}\label{fig:intense_rpi}
+  \end{figure}
 
@@
   antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
-  (Figure reference).  
+  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}).  
   \begin{itemize}
@@
   		of carboxylate groups attached to phenyl rings since the group extends the system's 
-  		$\pi$ conjugation. (citation)
-  		\item There are instances where carboxylates in other systems rotate out of plane.
+  		$\pi$ conjugation. (citation) (See figure in supporting info with energy barrier plots)
+  		\item There are instances where carboxylate groups in other systems rotate out of plane.
   		\item Bushey et al. showed that bulky carbonyl-containing substituents of stacked arene
@@
   pairs that stack less than 3.7 \AA apart, and whose center of masses are spaced 7.4 \AA 
-  from the next pair of monomers.(Figure reference)
+  from the next pair of monomers.(Figure ~\ref{fig:staggered_rzplot_norestraints})
   \begin{itemize}
@@
   		\degree$ with respect to the vector extending from the carboxylate carbon to the pore
-  		center.
+  		center (Figure ~\ref{fig:rotated_monomers_rzplot_norestraints})
   		\item Every other monomer layer is rotated $+15 \degree$ and those in between are
@@
 
-   %BJC3: 6 panel figure. Top 3 show each real space configuration in 3D. Bottom 3 show their
-   % simulated XRD patterns.
+  \begin{figure}[htb]
+  \centering
+  %BJC4: I could cut out the tails in the three real space configurations
+  %BJC4: I can remove some of the colorbars and state that they all follow the same color bar. 
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
+	\label{fig:rotated_carboxylate}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{staggered.png}
+	\label{fig:staggered}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers.png}
+  	\label{fig:rotated_monomers}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
+  	\label{fig:rotated_carboxylate_rzplot_restrained}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.png}
+  	\label{fig:staggered_rzplot_restrained}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
+  	\label{fig:rotated_monomers_rzplot_restrained}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
+  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
+  	%BJC4: needs to run longer
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png}
+  	\caption{}\label{fig:staggered_rzplot_norestraints}
+  	%BJC4: needs to be done
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
+  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
+  \end{subfigure}
+  \caption{R-double is present in all three inital configurations tested while the heavy atoms
+  in the headgroup are held in place with position restraints. R-double fades once 
+  the position restriants are released.}\label{fig:rdouble}
+  \end{figure}
 
@@
 
+  In general, the composition of the pores is similar between all systems. 
+  \begin{itemize}
+  	\item We believe we can study transport in any of the systems presented here and
+  	still extract valuable information.
+  	\item We will need to verify that this assumption is true.
+  \end{itemize}
+
   In all cases, the space in the pore region is filled with sodium ions and
@@
   (Figure~\ref{fig:xy_correlation}).
-  % High vacancy is less likely to be stable in the real system
 
@@
 
-  In general, the composition of the pores is similar between all systems. 
-  \begin{itemize}
-  	\item We believe we can study transport in any of the systems presented here and
-  	still extract valuable information.
-  	\item We will need to verify that this assumption is true.
-  \end{itemize}
-
   \begin{figure}
@@
 
-  END
+  END!!
 

### 2018-04-30 HII/Scripts/viscosity.py

@@ -8,6 +8,7 @@ import subprocess
 import os
 from pymbar import timeseries
 from scipy.optimize import curve_fit
+import tqdm
 
 
 def initialize():
@@ -24,17 +25,66 @@ def initialize():
     return args
 
 
-def autocorrelation(x):
-    """ FFT based autocorrelation function, which is faster than numpy.correlate
-    :param numpy array of y values of an equispaced timeseries
+def largest_prime_factor(n):
+    i = 2
+    while i * i <= n:
+        if n % i:
+            i += 1
+        else:
+            n //= i
+    return n
+
+
+def prime_factors(n):
+    i = 2
+    factors = []
+    while i * i <= n:
+        if n % i:
+            i += 1
+        else:
+            n //= i
+            factors.append(i)
+    if n > 1:
+        factors.append(n)
+    return factors
+
+
+def autocorrelation(x, largest_prime=500):
+    """ FFT based autocorrelation function, which is faster than numpy.correlate. Efficiency is key in order to avoid
+    headaches.
+    :param x : numpy array of y values of an equispaced timeseries
+    :param largest_prime : the largest prime factor of array length allowed. The smaller the faster. 1.6M points takes
+    about 5 seconds with largest_prime=1000. Just be aware that you are losing data by truncating. But 5-6 data points
+    isn't a big deal usually.
     """
 
+    # Force length of array to be power of 2
+    # powers = np.array([2 ** i for i in range(25)])
+    # closest = np.argmin(np.abs(powers - (2*x.size - 1)))
+    # nzeros = (powers[closest] // 2) - x.size
+    # if nzeros < 0:
+    #     closest += 1
+    #     nzeros = (powers[closest] // 2) - x.size
+    # v = np.concatenate((x, np.zeros([nzeros])))
+
+    # Just don't allow a prime factor larger than 'largest_prime'. Truncate data until that condition is met
+    l = 2*x.size - 1
+
+    while largest_prime_factor(l) >= largest_prime or l % 2 == 0:
+        l -= 1
+
+    x = x[:(l + 1) // 2]
     length = x.size*2 - 1
+
     fftx = np.fft.fft(x, n=length)
     ret = np.fft.ifft(fftx * np.conjugate(fftx))
     ret = np.fft.fftshift(ret)
 
-    return ret[length // 2:] / np.amax(ret[length//2:])
[…]

### 2018-05-01 Ben_Manuscripts/structure_paper/Outline.tex
New figures

@@
 
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{sodium_density.png}
+        \caption{Sodium Ions}
+        \label{fig:sodium_regional_density}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{head_group_density.png}
+        \caption{Head Groups}
+        \label{fig:head_groups_regional_density}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{tails_density.png}
+        \caption{Tails}
+        \label{fig:tails_regional_density}
+  \end{subfigure}
+  \caption{Alternate figure : In all cases, the component radial distribution functions exhibit a
+	  composition gradient transitioning from the hydrophilic to the hydrophobic
+	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
+	  displaced (a), and sandwiched (b) configurations both show the highest
+	  concentrations of ions and head groups away from the pore center. Systems with
+	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
+	  concentrations of ions and head groups near the pore center, implying a more
+	  uniform, disordered pore.}~\label{fig:overlaid_densities}
+  \end{figure}
+
   END!!

### 2018-05-08 Ben_Manuscripts/structure_paper/Draft.tex
Edits, organization, renamings, figure additions

@@
 
-  %MRS5: want to get people engaged from the beginning. The first paragraph
-  %should describe a problem to be solved. Then you can get into the motivating
-  %details (like background of the alternatives, and why we need something
-  %different).  I feel like this is an introduction into different types of
-  %membranes, though it should be an introduction to the problem that this paper
-  %takes steps towards solving.
-
-  Figure S~\ref{S-fig:monomer_color_coded}
+  % BJC5: Note to self -- how to use latex xr : Figure S~\ref{S-fig:monomer_color_coded}
 
@@
 
-%MRS6: I would keep a paragraph about here how current membranes DON'T
-%work for this purpose. But one paragraph is enough.x
-
 %  The permeability-selectivity tradeoff is a well-known problem in the membrane
@@
 
-%  Current commercial RO and NF membranes suffer from limitations inherent to
-%  their fabrication. Although scalable, each of these two types of membranes has
-%  a degree of stochasticity that makes overcoming the permeability-selectivity
-%  tradeoff a challenge. Namely, it is difficult to increase the permeability of
-%  a desired molecular or atomic species, while maintaining the same retention of
-%  an undesired species \cite{werber_materials_2016}.
+% MRS6: I would keep a paragraph about here how current membranes DON'T
+% work for this purpose. But one paragraph is enough.
+% BJC5: added back below paragraph
+  Current commercial RO and NF membranes suffer limitations to there selectivity 
+  which is inherent to their fabrication. Although scalable, each of these two types
+  of membranes has a degree of stochasticity that makes overcoming well-known the 
+  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
+  the permeability of a desired molecular or atomic species, while maintaining the same 
+  retention of an undesired species \cite{werber_materials_2016}.
 
@@
   strong membrane films with pores on the order of 1 nm in diameter
-  \cite{zhou_supported_2005}. Unlike commercial NF membranes, LLC membrane pores
+  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane pores
   are uniform in size. Since LLC membranes lack a pore size distribution, they
@@
   cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
-  %MRS6:
-  described in this paper
-  %chosen to make membranes for this application 
-  are salts, and therefore lead to
-  Donnan exclusion of ions in solution. The membrane gains a net surface charge
-  when counterions from head groups that line the pore walls escape into the feed
-  solution in order to balance the gradients of concentration and electric
-  potential \cite{donnan_theory_1995}.
+  described in this paper are salts, and therefore lead to Donnan exclusion of ions
+  in solution. The membrane gains a net surface charge when counterions from the head
+  groups that line the pore walls escape into the feed solution in order to balance 
+  the gradients of concentration and electric potential \cite{donnan_theory_1995}.
 
@@
   series of various sized dyes, the H\textsubscript{II} phase membrane showed
-  complete rejection of dyes bigger than 1.2 nm in size
-  \cite{zhou_supported_2005}.
-
-  The H\textsubscript{II} phase pore geometry is 
-%MRS6:
-%better 
-has a higher theoretical capacity
-for transport than the
-  Q\textsubscript{I} phase. The H\textsubscript{II} phase forms at room
-  temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
+  complete rejection of dyes bigger than 1.2 nm in size \cite{zhou_supported_2005}.
+
+  The H\textsubscript{II} phase pore geometry is has a higher theoretical capacity
+  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
+  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
   packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
@@
   promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
-  C when monomer is mixed with c.a.~20 wt\%
-  glycerol\cite{carter_glycerol-based_2012}. Q\textsubscript{I} phase membranes
-  consist of a tortuous network of three dimensionally interconnected pores that
-  prevent optimal through-plane transport. The densely packed, non-tortuous and
-  uniform sized pores of H\textsubscript{II} phase membranes represents the ideal
-  geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
+  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
+  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
+  interconnected pores that prevent optimal through-plane transport. The densely packed, 
+  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
+  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
   Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
-  liquid crystalline domains, formed during self-assembly of NA-GA3C11 monomers, are
-  isotropically aligned which is detrimental to membrane performance.
+  liquid crystalline domains, formed when Na-GA3C11 monomers self-assemble, are
+  isotropically aligned which is detrimental to membrane permeability.
 
@@
 
-%MRS5: not a strong thesis.  Why has it been revived?  The reasons for that would be a better thesis.
-  Recently, researchers have learned how to macroscopically align the hexagonal
-  domains which has revived research into H\textsubscript{II} phase LLC membranes.
 %  Research into the H\textsubscript{II} phase of polymerized LLC membranes has
@@
 %  For this reason, research efforts
+
+%MRS5: not a strong thesis.  Why has it been revived?  The reasons for that would be a better thesis.
+  Recently, researchers have learned how to macroscopically align the hexagonal
+  domains which has revived research into H\textsubscript{II} phase LLC membranes.
   Previously, research efforts were focused on the Q\textsubscript{I} phase,
@@
   can align Col\textsubscript{h} hexagonal domains using a magnetic field with
-  subsequent cross-linking to lock the structure in place
-  \cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
-  the same result using a second technique termed soft confinement
-  \cite{feng_thin_2016}. Current efforts are focused on extending the method to
-  the H\textsubscript{II} phase and characterizing the performance of these newly
-  aligned systems.
+  subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
+  In 2016, Feng et al. showed that one could obtain the same result using a second
+  technique termed soft confinement\cite{feng_thin_2016}. Current efforts are focused
+  on extending the method to the H\textsubscript{II} phase and characterizing the 
+  performance of these newly aligned systems.
 
@@
 
-  %BJC: Made my own version of the above, leaving out alignment details since it'
-
-  %BJC: TODO: Scalable vector graphic for monomer structure, make bigger. Convert .svg to .eps
-  %           Thicken slabs
-  %           Make pore region on slab (blue) bigger
-  %           Bump up atom sizes in atomistic render
+% BJC5 : This is how it is described in Xunda's papers. Should I shift to something
+% that doesn't rely on stacked disks? Maybe illustrate monomers stacked into
+% columns instead?
   \begin{figure}
@@
 
-  Our current understanding of 
-%MRS6:
-the molecular details of
-LLC membrane 
-%systems 
-nanostructure
-is not 
-%MRS6: 
-%rich enough to be
-sufficient
-  able to precisely design them for specific separations. Over the past 20 years,
-  H\textsubscript{II}-phase LLC polymer membrane studies have been limited
-  primarily to Na-GA3C11 with some characterization done after minor structural
-  modifications. Resel et al.~varied the length of the monomer tails and the
-  counterion used and observed its affect on pore spacing
-  \cite{resel_structural_2000}. In a later study of rejection performance, it was
-  shown that membranes formed by cross-linked Na-GA3C11 in the
-  H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in diameter
-  because the pores are too large \cite{zhou_supported_2005}. We do not yet
-  understand how to controllably reduce the effective pore size or how to tune
+  Our current understanding of the molecular details of LLC membrane nanostructure
+  is not sufficient to be able to precisely design them for specific separations. 
+  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane studies have
+  been limited primarily to Na-GA3C11 with some characterization done after minor 
+  structural modifications. Resel et al.~varied the length of the monomer tails and the
+  counterion used and observed its affect on pore spacing \cite{resel_structural_2000}.
+  In a later study of rejection performance, it was shown that membranes formed by cross-
+  linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes less than 1.2 
+  nm in diameter because the pores are too large \cite{zhou_supported_2005}. We do not
+  yet understand how to controllably reduce the effective pore size or how to tune
   the chemical environment in the nanopores of this or related materials for
@@
   counterions which may influence both the pore size and the strength of the
-  Donnan potential
-
+  Donnan potential. 
   %which affects the degree to which the membrane can exclude
@@
 	\end{subfigure}
-%MRS6: this is one place where I might go to passive voice, since anyone can only speculate not just us.  
-  \caption{We can only speculate about solute behavior inside the membrane
-	  pores based on our previous picture of the pore structure (a). 
-%MRS6: should be present text, not ``will use'' since it's what's happening in this paper. Look for this throughout.
-          We will use a
-	  detailed molecular model in order to appropriately model the pore's complex
-	  architecture which is crucial to understanding the mechanism of solute
-	  transport (b). The head group region is colored blue
-%MRS6: probably mention from actual simulations we will describe below.
-	  and the tail region is colored cyan in both representations.}~\label{fig:detail}
+    \caption{One can only speculate about solute behavior inside the membrane
+	  pores based on the previously established picture of the pore structure (a). 
+      We use a detailed molecular model in order to appropriately model the pore's
+      complex architecture which is crucial to understanding the mechanism of solute
+	  transport (b). The head group region is colored blue and the tail region is
+	  colored cyan in both representations. This image was generated from the molecular
+	  simulations run for this paper.}~\label{fig:detail}
   \end{figure}
 
-  Here we develop a model of the Col\textsubscript{h} assembly formed by
+  Here we develop a molecular model of the Col\textsubscript{h} assembly formed by
   Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
@@
   characterization of the fully aligned state, including 2D wide-angle X-ray
-  scattering (WAXS) patterns which are useful for reconstructing structural data.
-  We anticipate using this Col\textsubscript{h} model in order to build an 
+  scattering (WAXS) patterns (Figure\ref{fig:WAXS}) which are useful for reconstructing 
+  structural data. We will use this Col\textsubscript{h} model in order to build an 
   H\textsubscript{II} model in the future.
@@
 
-  In order to appropriately model transport in these ordered, nanoporous
-  organic systems, we must first gain a thorough understanding of the nanoscopic
-  structure of LLC polymer membranes. Our current level of understanding about
-  the structure at the nanoscale is limited. Using X-ray diffraction and TEM data
-  we can infer that monomers aggregate into hexagonally packed columns with their
-  head groups facing towards the column center. There remain several key questions
-  that we will investigate in order to expand this understanding:
+%  We used experimental small-angle X-ray scattering (SAXS) data from
+%  \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
+%  (WAXS) data (Fig.~\ref{fig:WAXS}, produced as described in
+%  \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
+%  since it encodes all structural details down to the sub-nm scale.  
+  There are five major features of interest present in the 2D experimental pattern shown 
+  in Figure \ref{fig:WAXS}.
 
   \begin{enumerate}
+
+	\item \textit{R-$\pi$}: The location of the first is at $q_z$ = 1.7
+	\AA$^{-1}$, corresponding to a real space separation of 3.7 {\AA}. Previous
+	work~\cite{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
+	stacking between aromatic rings in the direction perpendicular to the membrane
+	plane, or z-axis \cite{feng_scalable_2014}. For simplicity, we will refer to
+	this reflection as R-$\pi$.
+
+	\item \textit{R-double}: A weak intensity line, located at exactly half
+	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
+	space periodic spacing of 7.4 \AA~. Since this reflection corresponds to double
+	the spacing of R-$\pi$ in real space, will refer to this reflection as R-double. 
+	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
+	rings along the z axis\cite{feng_scalable_2014}, meaning that if one traces the 
+	positions of the aromatic rings with a helical curve, then for each full turn 
+	in the helix, one will encounter two aromatic rings.
+
+	\item \textit{R-alkanes}: A low intensity ring located at r = 1.4
+	\AA$^{-1}$ marks the third major reflection of interest. The real space
+	separation corresponds to 4.5 \AA~ which is characteristic of the average
+	spacing between packed alkane chains \cite{mcintosh_organization_1980}. We will
+	call this reflection R-alkanes.
+
+	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
+	relative intensity.  Accordingly, we name these reflection R-spots. The
+	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
+	respective quadrants. In many liquid crystal systems one can explain the spots
+	as the tilt angle of the alkane chains with respect to the membrane
+	plane\cite{govind_simple_2001}.
+
+	\item \textit{R-pores}: The final feature corresponds to the spacing
+	and symmetry of the d\textsubscript{100} plane. This plane is geometrically
+	related the distance between pores. The feature, which we named R-pores, is
+	characterized by dots along the equatorial axis defined when $q_z$ = 0. The
+	spacing between dots is indicative of the hexagonal symmetry of the packed
+	pores. We observe the same information with higher resolution using SAXS
+	(Fig.~\ref{fig:SAXS}).
+
+  \end{enumerate}
+
+  \begin{figure}
+        \centering
+        \begin{subfigure}[t]{0.43\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{SAXS.png}
+                \caption{}\label{fig:SAXS}
+        \end{subfigure}
+        \begin{subfigure}[t]{0.47\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
+                \caption{}\label{fig:WAXS}
+        \end{subfigure}
+	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
+		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
+		packing. The leading peak, q*, represents the distance between the
+		d\textsubscript{100} planes. Using this distance, we know that the distance
+		between pore centers is 4.12 nm. (b) 2D WAXS gives
+		details about repeating features on the order of angstroms. Experimentalists
+		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
+		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
+		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
+		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
+		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
+	\label{fig:SWAXS}
+ \end{figure}
+
+  Despite having structural data, there is still information which experiment cannot
+  definitively answer. There are a number of structural questions we wish to answer in this 
+  article. We want to know:
+  \begin{enumerate}
+    \item What is the density of monomers that pack around each hydrophilic core? 
+    \label{point:monomernum}
+
+ 	Authors often describe this and similar systems as being made up of layers. A simple
+ 	molecular simulation study of a similar molecule suggested that there are 4 monomers
+ 	in each layer. Their estimation is based on a simulated system containing only 16 total
+ 	monomers which likely does not sufficiently model the chemical environment present in
+ 	the real system.~\cite{zhu_methacrylated_2006}. A separate calculation based on the 
+ 	volume of the liquid crystal monomers proposes that there are seven monomers in each 
+ 	layer~\cite{resel_structural_2000}.
+
+ 	We are careful to avoid the term 'layers' since a liquid crystalline system has, by 
+ 	definition, long range order in 1 or 2 spatial dimensions and short range order in 	
+ 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
+ 	In the system we are studying, there are long-range 2D correlations in the 
+ 	hexagonal array of pores (xy plane) and short range correlations in the z-direction.
+ 	We will use our atomistic molecular model to study how the system's structure is 
+ 	effected by the density of monomers surrounding each pore's hydrophilic core.
+
+	\item What structural motif best matches experimental 2D WAXS patterns?\label{point:xrdmatch}
+
+	On the short timescales accessible to MD, we observe distinct metastable configurations
+	which depend on starting configuration. We simulated XRD patterns of our system and 
+	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS} so that we ensure our
+	model creates a nanoscopic chemical environment maximally consistent with experiment within 
+	the constraints	of our forcefield. Using this approach, we are able to confirm some previous
+	interpretations	of the WAXS pattern and refute others.
+
+	%BJC5: I could add brief references to other LLC studies which look at hexagnoal phase, but
+	% without scrutinizing the structural details. In other words, other authors have gotten 
+	% hexagonal phases with self-assembly, but they can't prove that their structure is the same
+	% as experiment. The best there are, are 1D structure factors in the small angle regime.
+
+	\item What is the chemical composition of the pores?\label{point:composition}
+
+	The limited picture that experiment provides tells us that there are hexagonally packed, 
+	hydrophilic regions where transport is likely to occur. One may instinctively imagine these 
+	regions as tube-like pathways with well-defined boundaries. We will explore the composition
+	of the pores, the partition between the hydrophilic and hydrophobic regions, and its 
+	sensitivity to initial configuration.
+
+    \item Is it necessary to include any water in order to appropriately model the 
+    Col\textsubscript{h} phase? \label{point:water}
+
+	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
+	ambient water may be leached into the system. The hydrogen bonding network formed by the 
+	water may play a role in structuring the pore. We used simulated X-ray diffraction patterns
+	to see if there is any meaningful structural difference between a "dry" and "wet" system.
+
+  \end{enumerate}
+
+%  In order to appropriately model transport in these ordered, nanoporous
+%  organic systems, we must first gain a thorough understanding of the nanoscopic
+%  structure of LLC polymer membranes. Our current level of understanding about
+%  the structure at the nanoscale is limited. Using X-ray diffraction and TEM data
+%  we can infer that monomers aggregate into hexagonally packed columns with their
+%  head groups facing towards the column center. There remain several key questions
+%  that we will investigate in order to expand this understanding: 
+%
+%  \begin{enumerate}
 
@@
 %  \item \textit{If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}} 
-  \item \textit{How many monomers pack around a single pore column?\label{point:monomernum}} 
-  A simple molecular simulation study of a similar molecule suggested that
-  4 monomers radially pack around hydrophilic pore columns \cite{zhu_methacrylated_2006}.
-  Their model likely does not sufficiently imitate the chemical environment present
-  in the real system since it only contains 16 total monomers. A separate calculation
-  for NA-GA3C11, based on the estimated volume of the liquid crystal monomers,
-  proposes that each pore is surrounded by seven
-  monomers\cite{resel_structural_2000}. Our best chance to answer this question
-  is by using a molecular model orders of magnitude larger than any other
-  reported atomistic liquid crystal membrane simulation, as we present here. We
-  will directly change the density of monomers in each pore and note its effect
-  on membrane structure.
-
-%  \item \textit{How do monomers in each layer position themselves with respect to
-%  surrounding layers? \label{point:orientation}}
-  \item \textit{In what orientation do monomer head groups stack on top of each
-  other \label{point:orientation} 
-  $\pi$-$\pi$ stacking interactions between aromatic monomer head groups may be
-  a driving force of self-assembly in this system \cite{gazit_possible_2002}. Gas
-  phase \textit{ab initio} studies of benzene dimers have shown a clear energetic
-  advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking
-  conformations over a sandwiched conformation \cite{sinnokrot_estimates_2002}.
-  Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking
-  attraction which favors the parallel displaced configuration in all cases except
-  where the substitutions are extremely electron withdrawing  
-  \cite{waller_hybrid_2006,ringer_effect_2006}. We did not consider the T-shaped 
-  configuration due to its geometric incompatibility with a hexagonal columnar phase.
-  The entropic contribution of the long alkane tails should overwhelm any attraction
-  between aromatic head groups in the T orientation. We limit our studies to
-  comparison of systems built in the parallel displaced and sandwiched configurations.
+%  \item \textit{How many monomers pack around a single pore column?\label{point:monomernum}} 
+%  A simple molecular simulation study of a similar molecule suggested that
+%  4 monomers radially pack around hydrophilic pore columns \cite{zhu_methacrylated_2006}.
+%  Their model likely does not sufficiently imitate the chemical environment present
+%  in the real system since it only contains 16 total monomers. A separate calculation
+%  for NA-GA3C11, based on the estimated volume of the liquid crystal monomers,
+%  proposes that each pore is surrounded by seven
+%  monomers\cite{resel_structural_2000}. Our best chance to answer this question
+%  is by using a molecular model orders of magnitude larger than any other
+%  reported atomistic liquid crystal membrane simulation, as we present here. We
+%  will directly change the density of monomers in each pore and note its effect
+%  on membrane structure.
+%
+%%  \item \textit{How do monomers in each layer position themselves with respect to
+%%  surrounding layers? \label{point:orientation}}
+%  \item \textit{In what orientation do monomer head groups stack on top of each
+%  other \label{point:orientation} 
+%  $\pi$-$\pi$ stacking interactions between aromatic monomer head groups may be
+%  a driving force of self-assembly in this system \cite{gazit_possible_2002}. Gas
+%  phase \textit{ab initio} studies of benzene dimers have shown a clear energetic
+%  advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking
+%  conformations over a sandwiched conformation \cite{sinnokrot_estimates_2002}.
+%  Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking
+%  attraction which favors the parallel displaced configuration in all cases except
+%  where the substitutions are extremely electron withdrawing  
+%  \cite{waller_hybrid_2006,ringer_effect_2006}. We did not consider the T-shaped 
+%  configuration due to its geometric incompatibility with a hexagonal columnar phase.
+%  The entropic contribution of the long alkane tails should overwhelm any attraction
+%  between aromatic head groups in the T orientation. We limit our studies to
+%  comparison of systems built in the parallel displaced and sandwiched configurations.
 
@@
 % BJC3:rephrasing everything about the above question. 
-  \item \textit{How strong are stacking correlations between monomer head groups?
-  \label{point:layers}}
+%  \item \textit{How strong are stacking correlations between monomer head groups?
+%  \label{point:layers}}
 
@@
 
-  \item \textit{What constitutes a pore, and what are the details of its composition?
-  \label{point:poredefinition}}
-  The limited picture that experiment provides tells us that there are
-  hexagonally packed, hydrophilic regions where transport is likely to occur.
-  One may instinctively assume that these regions are hollow tube-like pathways.
-  We will explore the composition of the pores and the partition between the
-  hydrophilic and hydrophobic regions.
-
-  \item \textit{Is it necessary to include any water in order to appropriately model
-  the Col\textsubscript{h} phase? \label{point:water}}
-  While past work describes the Col\textsubscript{h} phase as dry~\cite{feng_scalable_2014}, 
-  it has been suggested by experimentalists, in
-  unpublished communications, that it is likely that neat monomer leaches small
-  amounts of ambient water. Experimentally, achieving a hexagonal phase with a
-  completely dry system has proven difficult. If neat monomer sits in ambient
-  conditions, its color turns from transparent to slightly opaque and a hexagonal
-  phase forms. Although we will not explore whether water is necessary for
-  self-assembly, we hypothesize that the hydrogen bonding network formed by the
-  water may play a role in structuring the pores and holding together the
-  hexagonal phase. We can look at correlation functions and use simulated X-ray
-  diffraction patterns to see if there is any meaningful structural difference
-  between a ``dry'' and ``wet'' system.
-
-  \end{enumerate}
+%  \item \textit{What constitutes a pore, and what are the details of its composition?
+%  \label{point:poredefinition}}
+%  The limited picture that experiment provides tells us that there are
+%  hexagonally packed, hydrophilic regions where transport is likely to occur.
+%  One may instinctively assume that these regions are hollow tube-like pathways.
+%  We will explore the composition of the pores and the partition between the
+%  hydrophilic and hydrophobic regions. 
+% 
+%
+%  \item \textit{Is it necessary to include any water in order to appropriately model
+%  the Col\textsubscript{h} phase? \label{point:water}}
+%  While past work describes the Col\textsubscript{h} phase as dry~\cite{feng_scalable_2014}, 
+%  it has been suggested by experimentalists, in
+%  unpublished communications, that it is likely that neat monomer leaches small
+%  amounts of ambient water. Experimentally, achieving a hexagonal phase with a
+%  completely dry system has proven difficult. If neat monomer sits in ambient
+%  conditions, its color turns from transparent to slightly opaque and a hexagonal
+%  phase forms. Although we will not explore whether water is necessary for
+%  self-assembly, we hypothesize that the hydrogen bonding network formed by the
+%  water may play a role in structuring the pores and holding together the
+%  hexagonal phase. We can look at correlation functions and use simulated X-ray
+%  diffraction patterns to see if there is any meaningful structural difference
+%  between a ``dry'' and ``wet'' system.
+%
+%  \end{enumerate}
 
@@
 
-  We used experimental small-angle X-ray scattering (SAXS) data from
-  \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
-  (WAXS) data (Fig.~\ref{fig:WAXS}, produced as described in
-  \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
-  since it encodes all structural details down to the sub-nm scale.  There are
-  five major features of interest present in the 2D experimental pattern shown in
-  Figure \ref{fig:WAXS}.
-
-  \begin{enumerate}
-
-	\item \textit{R-$\pi$}: The location of the first is at $q_z$ = 1.7
-	\AA$^{-1}$, corresponding to a real space separation of 3.7 {\AA}. Previous
-	work~\cite{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
-	stacking between aromatic rings in the direction perpendicular to the membrane
-	plane, or z-axis \cite{feng_scalable_2014}. For simplicity, we will refer to
-	this reflection as R-$\pi$.
-
-	\item \textit{R-helix}: A weak intensity line, located at exactly half
-	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
-	space periodic spacing of 7.4 \AA~. This reflection has been interpreted as
-	2\textsubscript{1} helical ordering of aromatic rings along the z axis
-	\cite{feng_scalable_2014}, meaning that if one traces the positions of the
-	aromatic rings with a helical curve, then for each full turn in the helix, one
-	will encounter two aromatic rings. For this reason we will refer to reflection
-	as R-helix.
-
-	\item \textit{R-alkanes}: A low intensity ring located at r = 1.4
-	\AA$^{-1}$ marks the third major reflection of interest. The real space
-	separation corresponds to 4.5 \AA~ which is characteristic of the average
-	spacing between packed alkane chains \cite{mcintosh_organization_1980}. We will
-	call this reflection R-alkanes.
-
-	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
-	relative intensity.  Accordingly, we name these reflection R-spots. The
-	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
-	respective quadrants. In many liquid crystal systems one can explain the spots
-	as the tilt angle of the alkane chains with respect to the membrane
-	plane\cite{govind_simple_2001}.
-
-	\item \textit{R-pores}: The final feature corresponds to the spacing
-	and symmetry of the d\textsubscript{100} plane. This plane is geometrically
-	related the distance between pores. The feature, which we named R-pores, is
-	characterized by dots along the equatorial axis defined when $q_z$ = 0. The
-	spacing between dots is indicative of the hexagonal symmetry of the packed
-	pores. We observe the same information with higher resolution using SAXS
-	(Fig.~\ref{fig:SAXS}).
-
-  \end{enumerate}
-
-  \begin{figure}
-        \centering
-        \begin{subfigure}[t]{0.43\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{SAXS.png}
-                \caption{}\label{fig:SAXS}
-        \end{subfigure}
-        \begin{subfigure}[t]{0.47\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
-                \caption{}\label{fig:WAXS}
-        \end{subfigure}
-%BJC: What do you think of the labels now? I tried to make it more clear what each label refers
-% to graphically. I can't decide if it's too cluttered. An alternative is to number them as  
-% I had them before, and then define them in a little box inset to the figure
-	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
-		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
-		packing. The leading peak, q*, represents the distance between the
-		d\textsubscript{100} planes. Using this distance, we know that the distance
-		between pore centers is 4.12 nm. (b) 2D WAXS gives
-		details about repeating features on the order of angstroms. Experimentalists
-		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
-		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-helix) Monomers arrange vertically in
-		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
-		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
-		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
-	\label{fig:SWAXS}
- \end{figure}
-
   \section{Methods}
@@
 
-  We parameterized the liquid crystal monomers using the Generalized AMBER
-  Force Field \cite{wang_development_2004} with the Antechamber package
+  We parameterized the liquid crystal monomer Na-GA3C11 using the Generalized AMBER
+  Force Field (GAFF) \cite{wang_development_2004} with the Antechamber package
   \cite{wang_automatic_2006} provided with AmberTools16
@@
   configuration from the trajectory which we used for full system
-  construction (Figure~\ref{fig:python}a). See Supporting Information for
-  further detail.
+  construction (Figure~\ref{fig:python}a). See section S-\ref{S-section:parameterization} 
+  for further detail.
 
@@
   \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system. To bypass the slow
-  self-assembly process, we use Python scripts to assemble monomers into a
-  structure close to one of a number of hypothesized equilibrium configurations
+  indicators of progress towards an ordered system (See supporting information). 
+  %BJC5: section showing self-assembly set up to be added
+  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
+  into a structure close to one of a number of hypothesized equilibrium configurations
   (Figure~\ref{fig:python}).
-  %MRS6: question; we would like to make these releasable in GitHub.
-  %BJC2: yes .. what is the question?
+
+  % BJC5: This needs to be modified to reflect columnar build procedure
   \begin{figure}
@@
 	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
-		configuration. (b) A Python script rotates and assembles monomers into layers with 
-		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
-		pores. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
+		configuration. (b) A Python script assembles monomers into columns which are duplicated 
+		and rotated to surround hydrophilic pore centers. (c) We chose to stack twenty monomers
+		into each column. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
   \end{figure}
@@
   the smallest unit cell that maintains hexagonal symmetry when extended
-  periodically. Each pore is made of twenty stacked monomer layers with periodic
+  periodically. Each pore is made of columns of stacked monomers with periodic
   continuity along the pore axis, avoiding any edge effects and creating an
-  infinite length pore ideal for studying transport. We prefer a small number of layers
-  in order to reduce computational cost and to allow us to look at
-  longer timescales. Ultimately, we chose to build a system with 20 monomer
-  layers in each pore in order to obtain sufficient resolution when simulating
+  infinite length pore ideal for studying transport. We prefer a small number stacked
+  monomers in order to reduce computational cost and to allow us to look at
+  longer timescales. Ultimately, we chose to build a system with 20 monomers
+  per column in order to obtain sufficient resolution when simulating
   X-ray diffraction patterns. %This point will be explained in more detail later.
-%MRS3: isn't there some observations you need at least 10?  
-%BJC2: When I first set up the system, there was a gap and a small number of layers 
-% appeared to cause the phase to disassociate. However, I can get a pretty small
-% number of layers in the infinite pore system, but the diffraction is low resolution.
 
@@
   a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
-  configurations. 
-  %MRS6: added.
-  The initial distance between pores, within a wide range, also has little effect on
-  the the equilibrated structure. However, one should not start them too close or
-  there will be high energy repulsions during early equilibration. We chose an
-  initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
-  of 4.12 nm.  A sensitivity analysis of both parameters is presented in
-  the 
-  %MRS6: check for J phys chem B to see if its supporting or supplemental information or material.
-  %BJC2: good point. It is 'supporting information'
-  Supporting information.  The distance between layers, the rotation of the
-  layers with respect to adjacent layers, and the number of monomers per layer do
-  influence the equilibrium structure and require further justification for their
-  choices. We rely on experimental data to inform them.
-
-  We chose the layer spacing for the initial configuration based on R-$\pi$ and
-  then allowed the system to readjust during equilibration. Each monomer was
-  rotated so the plane of its aromatic head groups would be coplanar with the xy
-  plane. We explored three different initial layer spacings. The first is exactly
+  configurations. The initial distance between pores, within a wide range, also has 
+  little effect on the the equilibrated structure. However, one should not start them
+  too close or there will be high energy repulsions during early equilibration. We 
+  chose an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
+  of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
+  Supporting information, section S-\ref{S-section:initial_config_dependence}. The 
+  distance between vertically stacked monomers, the position of monomers with respect 
+  to vertically adjacent monomers, and the number of columns per pore do influence the 
+  equilibrated structure and require further justification for their choices. We rely on 
+  experimental data to inform them.
+
+  We chose the vertical spacing between monomers for the initial configuration based
+  on R-$\pi$ and then allowed the system to readjust during equilibration. Each monomer was
+  rotated so the plane of its aromatic head groups would be coplanar with the xy plane. We
+  explored three different initial monomer spacings. The first is exactly
   equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
-  the z-direction. We explore a second system with an initial layer spacing of 5
-  \AA. We briefly explored a third system with an initial layer spacing of 10
+  the z-direction. We explore a second system with an initial spacing of 5
+  \AA. We briefly explored a third system with an initial spacing of 10
   \AA, however it shows non-physical behavior which is detailed in the 
-  Supporting Information.
+  Supporting Information, section S-\ref{S-section:initial_dbwl}.
 
@@
 
-  We chose the relative interlayer orientation based on clues from diffraction
-  data as well as the various known stacking modes of benzene and substituted
-  benzene rings: sandwiched, parallel-displaced and T-shaped
+  We chose the relative orientation between vertically adjacent monomers in each column 
+  based on clues from diffraction data as well as the various known stacking modes of 
+  benzene and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
   \cite{sinnokrot_estimates_2002}. We ruled out the T-shaped configuration
-  because its $\sim$5 \AA~equilibrium stacking distance
-  \cite{sinnokrot_estimates_2002} is inconsistent with R-$\pi$. It is also
-  infeasible for the monomers to orient in the T-shaped conformation because of
-  the bulky tail groups. We will explore the system's preference towards the
-  sandwiched vs. parallel displaced stacking modes in some detail. Both have
-  reported stacking distances near the R-$\pi$ value of 3.7 \AA. Headgroups in
+  because its $\sim$5 \AA~equilibrium stacking distance \cite{sinnokrot_estimates_2002}
+  is inconsistent with R-$\pi$. It is also infeasible for the monomers to orient in the 
+  T-shaped conformation because of the bulky tail groups. We will explore the system's 
+  preference towards the sandwiched vs. parallel displaced stacking modes in some detail.
+  Both have reported stacking distances near the R-$\pi$ value of 3.7 \AA. Head groups in
   our sandwiched initial configuration stack directly on top of each other while
-  headgroups in the parallel displaced initial configuration stack with an offset
-  of $180^\circ/nmon$ where $nmon$ is the number of monomers per layer. See
-  the Supporting Information for a detailed illustration of the initial
+  head groups in the parallel displaced initial configuration stack with an offset
+  of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See the Supporting
+  Information, Figure~\ref{S-fig:stacking} for a detailed illustration of the initial
   configurations in each mode.
 
-  The number of monomers in each layer is unknown, as stated in question
+  % BJC5: figure here illustrating parallel displaced vs. sandwiched?
+
+  The number of columns per pore is unknown, as stated in question
   (\ref{point:monomernum}). We tested configurations constructed with a varied
-  number of monomers per layer. We built systems in the offset and parallel
+  number of columns per pore. We built systems in the offset and parallel
   displaced configurations with 4, 5, 6, 7 and 8 monomers per layer.
@@
 
-  %MRS6: some parameters missing here (time run between insertions, etc). 
-  %I assume they are in supporting information?
-  %BJC2: Not there yet but will add
+  % MRS6: some parameters missing here (time run between insertions, etc). 
+  % I assume they are in supporting information?
+  % BJC5: all water is present in initial configuration. This did not follow the more
+  % complex procedures that I've come up with since then. 
   In order to create a ``wet'' system, we solvated an initial configuration with
@@
 
-  \subsection{Cross-linking}
-
-  In order to fully match synthetic procedures, we created a cross-linking
-  algorithm that one can apply to equilibrated structures. The purpose of
-  cross-linking is to maintain macroscopic alignment of the crystalline domains,
-  ensuring aligned, hexagonally packed pores. For that reason, we are not
-  concerned with replicating the kinetics of the reaction, but instead emphasize
-  the consistency of the final structure with experimental structural data.
-
-  We developed the algorithm based on the known reaction mechanism.
-  Cross-linking of this system is a free radical polymerization (FRP) taking
-  place between terminal vinyl groups present on each of the three monomer tails.
-  FRPs require an initiator which bonds to the system, meaning new atoms are
-  introduced into the system. For simplicity, we simulated the initiator as
-  hydrogen and made it present in the simulation by including them as dummy atoms
-  in all possible locations where an addition could occur. We carry out the
-  cross-linking procedure iteratively. During each iteration, the algorithm
-  selects eligible bonding carbon atoms based on a distance cut-off. The topology
-  is updated with new bonds and dummy hydrogen atoms are changed to appropriate
-  hydrogen types.  Head-to-tail addition was the only propagation mode considered
-  due to its dominance in the real system \cite{young_introduction_2011}. We did
-  not consider direction of attack because the resultant mixture is racemic.
-
-  Our implementation requires long simulation times to achieve high cross-link 
-  densities. A typical cross-linking procedure can take up to 24 hours. In
-  order to collect equilibrated data, further NPT simulation is necessary. We
-  typically run a cross-linked system for an additional 100 ns to allow the system
-  to readjust. For those reasons we did not cross-link all systems tested, but only
-  the most promising structure. We show that cross-linking does not significantly
-  change any of our drawn conclusions in Section 3.6.
-
   \subsection{Equilibrium Calculations}
 
-  \subsubsection{\textit{Determining equilibration time}}
+  \subsubsection{\textit{Determining equilibration time}}\label{method:equil_time}
 
@@
 
-  \subsubsection{\textit{Calculation of pore spacing}}
+  \subsubsection{\textit{Calculation of pore spacing}}\label{method:pore_spacing}
 
@@
   ions in their respective pores. We generated pore spacing statistics 
-  using the bootstrapping technique (See Supporting Information).
-
-  \subsubsection{\textit{The nematic order parameter}}
-
-  We calculated the nematic order parameter for our system in order to
-  understand the degree of ordering among monomer head groups. Typically, the
-  nematic order parameter is calculated for nematic liquid crystal systems which
-  are characterized by unidirectional ordering of liquid crystal monomers. The
-  preferred direction of monomers is defined by the unit director vector,
-  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
-  order parameter, $S$, is defined as:
-  \begin{equation}
-	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
-	\label{eqn:nematic_order_parameter}
-  \end{equation}
-  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
-  In a perfectly ordered system, the molecular axis should be aligned with
-  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
-  quantifying the degree of monomer head group alignment between systems. We use
-  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
-  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
-  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
-  the aromatic head groups. See the Supporting Information for a diagram.
-
-  \subsubsection{\textit{Pair distribution functions}}
+  using the bootstrapping technique (See section S-\ref{S-section:p2p_stats} of the
+  Supporting Information).
+
+  %BJC5: moved to supporting info
+%  \subsubsection{\textit{The nematic order parameter}}\label{method:nematic_order}
+%
+%  We calculated the nematic order parameter for our system in order to
+%  understand the degree of ordering among monomer head groups. Typically, the
+%  nematic order parameter is calculated for nematic liquid crystal systems which
+%  are characterized by unidirectional ordering of liquid crystal monomers. The
+%  preferred direction of monomers is defined by the unit director vector,
+%  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
+%  order parameter, $S$, is defined as:
+%  \begin{equation}
+%	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
+%	\label{eqn:nematic_order_parameter}
+%  \end{equation}
+%  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
+%  In a perfectly ordered system, the molecular axis should be aligned with
+%  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
+%  quantifying the degree of monomer head group alignment between systems. We use
+%  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
+%  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
+%  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
+%  the aromatic head groups. See the Supporting Information for a diagram.
+
+  \subsubsection{\textit{Pair distribution functions and correlation length}}\label{section:correlation_length}
 
@@
   We applied equation \ref{eqn:correlation} in three dimensions and then
-  extracted one and two dimensional distribution functions by collapsing the grid
-  along the appropropriate axes.
-
-  In the 1D case, we measured the pair distribution function between centers of
-  masses of aromatic head group rings, $g(z)$, along the z-axis (perpendicular to
-  the membrane plane). To extract the average distance between layers we applied
-  a discrete Fourier transform to $g(z)$ and extracted the highest intensity
-  frequency. We performed the same procedure to calculate $g(z)$ of the tails 
-  except instead of using the center of masses of the tails, we averaged $g(z)$
-  for each atom that makes up the tail.
-
-  In two dimensions, we observed xy and xz pair distribution functions based on
-  the center of masses of the aromatic head group rings. For the xy pair
-  distribution functions, we used a rotated frame of reference. For a given center
-  of mass, we rotated the coordinates so that the vector created from the center
-  of mass to the pore center was aligned with the positive x-axis.
+  extracted one dimensional distribution functions using slices of the grid
+  along the appropriate axis.
+
+  We measured the one dimensional pair distribution function, $g(z)$, between centers 
+  of masses of aromatic head group rings along the z-axis (perpendicular to
+  the membrane plane). We averaged all 1D slices in the z-direction of the full 3D 
+  correlation function within 2.1~\AA~of $(x, y)=(0, 0)$. We chose 2.1 \AA as a crude 
+  approximation of the radius of the phenyl ring plane. 
+  %In this way, we include any instances of 
+  %overlapping electron density which would contribute to R-$\pi$. 
+  We calculated the radius as the sum of the longest C-C distance within a phenyl 
+  ring (2.8~\AA) and two times the carbon atom radius (0.7~\AA).
+
+  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
+  average distance between stacked monomers, and an amplitude that decays exponentially
+  (See Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
+  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
+  to a decaying exponential function of the form:
+  \begin{equation}
+  	Ae^{-z/L}
+  \end{equation}
+  where A is a fitting parameter for amplitude, z is the independent variable of $g(z)$ 
+  and L is the fit correlation length. The error in the estimated value of L is 
+  calculated as the square root of the diagonal entry of the covariance matrix of 
+  optimized fit parameters.
+
+% BJC5: I don't plan on showing any 2D correlation functions -- maybe to show swelling
+% of solvated systems.
+
+%  In two dimensions, we observed xy and xz pair distribution functions based on
+%  the center of masses of the aromatic head group rings. For the xy pair
+%  distribution functions, we used a rotated frame of reference. For a given center
+%  of mass, we rotated the coordinates so that the vector created from the center
+%  of mass to the pore center was aligned with the positive x-axis.
 
@@
   \subsubsection{\textit{Radial distribution functions}}
-  Closely related to the spatial correlation functions, we explored the pores'
-  compositions by measuring the average number densities of various monomer
-  components as a function of distance from the pore centers. We looked at the
-  average number density of sodium ions, aromatic rings and carbon atoms making
-  up the monomer tails. We binned the radial distance of all atoms in each group
-  from the pore centers, then normalized by the volume of the annulus defined by
-  the bin edges and the z box vector (See Supporting Information for a 
-  diagram).
+
+  We explored the pores' compositions by measuring the average number densities
+  of various monomer components as a function of distance from the pore centers.
+  We looked at the average number density of sodium ions, aromatic rings and 
+  carbon atoms making up the monomer tails. We binned the radial distance of all
+  atoms in each group from the pore centers, then normalized by the volume of the
+  annulus defined by the bin edges and the z box vector (See Figure~\ref{S-fig:rdf_diagram}
+  in the Supporting Information).
 
   \subsubsection{\textit{Simulated structure factor calculations}}
-  % BJC: To be replaced by Joe's description
-  {\color{red}This section replaced by Yelk/Glaser text}. 
-  Simulated X-ray diffraction patterns are generated based on atomic
+
+  Simulated X-ray diffraction patterns were generated based on atomic
   coordinates in order to make a direct experimental comparison. All atomic
   coordinates were simulated as Gaussian spheres of electron density
-  corresponding to each atom's atomic number. A three dimensional Fourier
+  corresponding to each atom's electronic radius. A three dimensional Fourier
   transform (FT) of the array of electron density results in a three dimensional
-  structure factor which represents the unit cell in reciprocal space. We matched
-  experimental 2D WAXS patterns by adjusting the initial spacing between layers
-  and the orientation of the head groups with respect to adjacent layers.
-
-  We normalized the colorbars on all diffraction patterns relative to
-  R-alkanes. We believe that the alkane-alkane density, averaged over all angles,
-  is the feature most likely to be replicated between experiment and simulation.
-  Other features are dependent on system ordering which is likely to have some
-  dependence on initial configuration. We calculated the average intensity within
-  R-alkanes of the experimental pattern, $I_{avg}$. We exclude intensities within
-  $\pm$ 30\degree~of the meridional axis defined by $q_r=0$ , since the simulated
-  patterns differ from experiment in those regions in all cases. Specifically, in
-  contrast to the experimental WAXS pattern, R-$\pi$ appearing in simulated
-  diffraction patterns intersects with R-alkanes (See Fig. \ref{fig:XRDsim}). We
-  multiplied $I_{avg}$ by a scaling factor, $f$. Intensities that appear in the
-  experimental pattern $\geq$ $f\times I_{avg}$ are colored uniformly. We apply
-  the same scaling method to the simulated patterns. We carefully chose a scaling
-  factor of $f=3.1$ in order to (1) visibly display all features in the
-  experimental pattern and (2) to allow us to compare the relative intensities of
-  features between simulated and experimental diffraction patterns.
+  structure factor which represents the unit cell in reciprocal space. The
+  experimental WAXS measurement was made using a vertically aligned film whose 
+  pores were oriented perpendicular to the direction of the incident X-ray beam. 
+  Although the pores were vertically aligned, the crystalline domains were still
+  misaligned with respect to the xy plane. To account for this, we averaged
+  2D slices of the structure factor at all angles about $|\mathbf{q}| = (0, 0, z)$.
+
+  We normalized all diffraction patterns relative to R-alkanes. We believe that the
+  alkane-alkane density, averaged over all angles, is the feature most likely to be
+  replicated between experiment and simulation. Other features are dependent on 
+  system ordering which is likely to have some dependence on initial configuration. 
+  We calculated the average intensity within R-alkanes of the experimental pattern,
+  $I_{avg}$ and divide all intensities by this values. In this way, the average intensity
+  of the alkanes is equal to 1. When calculating $I_{avg}$, we excluded intensities 
+  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the simulated
+  patterns differ from experiment in those regions in all cases. Specifically, in contrast
+  to the experimental WAXS pattern, R-$\pi$ appearing in simulated diffraction patterns 
+  intersects with R-alkanes (See Fig. \ref{fig:XRDsim}). We set
+  an upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$. 
+  Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored uniformly. 
+  We apply the same scaling method to the simulated patterns. We carefully chose a scaling
+  factor of $f=3.1$ in order to visibly display all features in the all patterns.
 
@@
 
+  \subsection{Cross-linking}
+
+  In order to fully match synthetic procedures, we created a cross-linking
+  algorithm that one can apply to equilibrated structures. The purpose of
+  cross-linking is to maintain macroscopic alignment of the crystalline domains,
+  ensuring aligned, hexagonally packed pores. For that reason, we are not
+  concerned with replicating the kinetics of the reaction, but instead emphasize
+  the consistency of the final structure with experimental structural data.
+
+  %BJC5: perhaps this paragraph should be moved to supporting info.
+  We developed the algorithm based on the known reaction mechanism.
+  Cross-linking of this system is a free radical polymerization (FRP) taking
+  place between terminal vinyl groups present on each of the three monomer tails.
+  FRPs require an initiator which bonds to the system, meaning new atoms are
+  introduced into the system. For simplicity, we simulated the initiator as
+  hydrogen and made it present in the simulation by including them as dummy atoms
+  in all possible locations where an addition could occur. We carry out the
+  cross-linking procedure iteratively. During each iteration, the algorithm
+  selects eligible bonding carbon atoms based on a distance cut-off. The topology
+  is updated with new bonds and dummy hydrogen atoms are changed to appropriate
+  hydrogen types.  Head-to-tail addition was the only propagation mode considered
+  due to its dominance in the real system \cite{young_introduction_2011}. We did
+  not consider direction of attack because the resultant mixture is racemic.
+
+  Our implementation requires long simulation times to achieve high cross-link 
+  densities. A typical cross-linking procedure can take up to 24 hours. In
+  order to collect equilibrated data, further NPT simulation is necessary. We
+  typically run a cross-linked system for an additional 100 ns to allow the system
+  to readjust. For those reasons we did not cross-link all systems tested, but only
+  the most promising structure. We show that cross-linking does not significantly
+  change any of our drawn conclusions in Section 3.6.
+
   \section{Results and Discussion}
 
-  \subsection{Structural Characterization}
-
-  \subsubsection{Density of monomers around pores}
-
-  Our simulations best support a model built with 5 monomers per layer based on
+  \subsection{Density of monomers around pores}
+
+% BJC5: old
+%  Our simulations best support a model built with 5 monomers per layer based on
+%  the measured equilibrated pore-to-pore distances. To discern the composition of
+%  the monomer layers, addressing question (\ref{point:monomernum}), we ran
+%  simulations of systems created with 4--8 monomers per layer. We built systems
+%  in both the parallel displaced and sandwiched configurations with layers
+%  initially spaced 3.7 \AA~apart. We prepared equilibrated configurations
+%  according to the dry equilibration procedure. The pore-to-pore spacing is stable
+%  in all systems are stable after 400 ns of simulation. Figure~\ref{fig:p2p} shows
+%  the equilibrated pore-to-pore distances for all systems tested. Systems built 
+%  with 5 monomers in each layer equilibrate to a pore spacing that is most consistent
+%  with the experimental value of 4.12 nm derived from SAXS measurements 
+%  (Figure~\ref{fig:SAXS}).
+%  
+%  The remainder of this discussion will focus on the analysis of systems built with
+%  5 monomers per layer. Systems built with 6 monomers per layer have an equilibrated
+%  pore spacing c.a. 0.50 nm higher than experiment. Systems built with 4 monomers per 
+%  layer equilibrate to a pore spacing 0.25 nm lower than experiment. In a sense, all
+%  systems tested are at least metastable, however not all will make physical
+%  sense or fit the experimental profile that we are trying to match. In the limit of
+%  infinite time, all simulations will converge to a single density. It is our 
+%  intention to choose an initial configuration which quickly reaches a monomer density
+%  close to experiment.
+
+  % BJC5: trying things out with 'columns per pore' instead of 'monomers per layer'.
+  Our simulations best support a model built with 5 monomer columns per pore based on
   the measured equilibrated pore-to-pore distances. To discern the composition of
   the monomer layers, addressing question (\ref{point:monomernum}), we ran
-  simulations of systems created with 4--8 monomers per layer. We built systems
-  in both the parallel displaced and sandwiched configurations with layers
-  initially spaced 3.7 \AA~apart. We prepared equilibrated configurations
-  according to the dry equilibration procedure. The pore-to-pore spacing is stable
-  in all systems are stable after 400 ns of simulation. Figure~\ref{fig:p2p} shows
-  the equilibrated pore-to-pore distances for all systems tested. Systems built 
-  with 5 monomers in each layer equilibrate to a pore spacing that is most consistent
-  with the experimental value of 4.12 nm derived from SAXS measurements 
+  simulations of systems created with 4--8 columns per pore. We built systems in both
+  %BJC5: need to make parallel displaced and sandwiched configurations clear in methods
+  the parallel displaced and sandwiched configurations and equilibrated them according
+  to the dry equilibration procedure. We test all systems with an initial vertical monomer 
+  spacing, \textit{d}, of 3.7~\AA in accordance with R-$\pi$. We tested 4 additional systems with
+  monomers initially spaced 5 \AA~apart vertically (See supporting info for more details on       
+  %BJC5: integrate supplemental section labels into main paper.
+  sensitivity to initial layer spacing). The pore-to-pore spacing is equilibrated, as defined in
+  section~\ref{method:equil_time} in all systems after 400 ns of simulation.
+  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested. 
+  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most
+  %BJC5: New paragraph? 
+  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
   (Figure~\ref{fig:SAXS}).
+  %BJC5: comment about disordered systems
 
   The remainder of this discussion will focus on the analysis of systems built with
-  5 monomers per layer. Systems built with 6 monomers per layer have an equilibrated
-  pore spacing c.a. 0.50 nm higher than experiment. Systems built with 4 monomers per 
-  layer equilibrate to a pore spacing 0.25 nm lower than experiment. In a sense, all
-  systems tested are at least metastable, however not all will make physical
-  sense or fit the experimental profile that we are trying to match. In the limit of
-  infinite time, all simulations will converge to a single density. It is our 
-  intention to choose an initial configuration which quickly reaches a monomer density
-  close to experiment.
+  5 columns per pore. Systems built with 6 columns per pore have an equilibrated
+  pore spacing c.a. 0.50 nm higher than experiment. Systems built with 4 columns per pore
+  %BJC5: edit above with consciencenous of new 6 mon/layer sim data
+  equilibrate to a pore spacing 0.25 nm lower than experiment. All systems tested are at least
+  metastable on the timescales studied here, however not all make physical sense or
+  fit the experimental profile that we are trying to match. In the limit of infinite simulation
+  time, all simulations will converge to a single density. It is our intention to choose an
+  initial configuration which quickly reaches a monomer density close to experiment. We believe
+  systems built with 5 columns per pore achieve this goal.
 
@@
 	\includegraphics[width=\linewidth]{p2p.png}
-        %MRS6: should there be a grapical demonstration of sandwiched vs. parallel displaced, especially equilbrated?
-        % BJC3: I have that in the supplemental information. I could move it into the main
-        % body. I think it would be best in the intro where I pose the question of parallel 
-        % displaced v. sandwiched.
-	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
+	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
 			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
-			 increases as the number of monomers in each layer increases. The pore spacing
+			 increases as the number of columns in each pore increases. The pore spacing
 			 of systems starting in the sandwiched configuration are systematically lower
+			 %BJC5: double check this statement once all data is present
 			 than those started in the parallel displaced configuration.}~\label{fig:p2p}
@@
 
-%  \subsubsection{Relative interlayer head group orientation}
-  \subsubsection{Structural refinement}
+  \subsection{Structural refinement with 2D WAXS data}
 
@@
   diffraction patterns produced from equilibrated MD trajectories and comparing them
-  to experiment. We tested systems built with 5 monomers per layer in the parallel 
-  displaced and sandwiched configurations at 300K. We generated simulated patterns using 
-  portions of simulation trajectory after equilibration. The patterns for both 
-  structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
-
-  Simulated XRD of the sandwiched configuration shows most all experimental features 
-  except R-helix and R-spots. R-pores and R-alkanes appear in their expected locations. 
-  R-pores is more intense than experiment, likely because we are simulating a perfect,
-  infinite hexagonal array. The real system has defects and domain misalignment
-  which decreases the overall intensity. R-$\pi$ appears with very high intensity and
-  is shifted down to a lower value of $q_z$ meaning monomers in our model prefer to 
-  stack farther apart.
-
-  Simulated XRD of the sandwiched configuration contains all experimental
-  features except for R-helix. R-alkanes, R-spots and R-pores appear close to their
-  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
-  a $q_z$ value lower than experiment meaning the head groups in our model prefer 
-  to stack farther apart.
-
-  Like the sandwiched configuration, the parallel displaced configuration creates
-  a simulated XRD pattern with all major experimental reflections except for R-helix.
-  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
-  and R-$\pi$ appear, however with a lower intensity
-  relative to R-alkanes when compared to the sandwiched configuration. R-helix
-  appears due to the parallel displaced aromatic rings. It is a subharmonic of
-  R-$\pi$ since the nearest vertically stacked head group to any given head group
-  is $2\times$R-$\pi$~away. 
-  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
-  \begin{figure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \vspace{-0.2em}
-        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{offset_rzplot.png}
-        \caption{}~\label{fig:rz_offset}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-%        \vspace{0.25em}
-        \includegraphics[scale=0.285]{WAXS_raw.png}
-        \caption{}~\label{fig:raw_waxs}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-        \centering
-        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{layered_rzplot.png}
-        \caption{}~\label{fig:rz_layered}
-  \end{subfigure}
-  \begin{subfigure}{0.0544\linewidth}
-        \centering
-        \vspace{-4.00em}
-        \includegraphics[width=\linewidth]{colorbar_seismic.png}
-  \end{subfigure}
-%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced.
+  to experiment. We tested systems built with 5 columns per pore in the parallel 
+  displaced and sandwiched configurations at 300 K with monomers initially stacked
+  3.7 \AA~and 5.0 \AA~apart. We generated simulated patterns using portions
+  of simulation trajectory after equilibration. The patterns for all structures are
+  shown and compared to experiment in Figure~\ref{fig:XRDsim}.
+
+  %BJC5: put figure letters in upper left hand corner of each pattern.
+  \begin{figure}[htb]
+	\centering
+	\begin{subfigure}{0.88\textwidth}
+	\begin{subfigure}{0.28\linewidth}
+			\begin{subfigure}{\textwidth}
+			\centering
+		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
+			        %\caption{Sandwiched}~\label{fig:rzplot_layered_300K}
+			\end{subfigure}
+			\begin{subfigure}{\textwidth}
+		       		\centering
+	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
+	        		%\caption{Disordered sandwiched}~\label{fig:rzplot_layered_300K}
+			\end{subfigure}
+	\end{subfigure}
+	\begin{subfigure}{0.4\linewidth}
+	\centering
+			\begin{subfigure}{\textwidth}
+		       		\centering
+	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
+	        		%\caption{Experimental WAXS}~\label{fig:offset_tails}
+			\end{subfigure}
+	\end{subfigure}
+	\begin{subfigure}{0.28\linewidth}
+	\centering
+			\begin{subfigure}{\textwidth}
+			\centering
+		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
+			        %\caption{Parallel displaced}~\label{fig:rzplot_offset_300K}
+			\end{subfigure}
+
+			\begin{subfigure}{\textwidth}
+			\centering
+		    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
+			        %\caption{Disordered parallel displaced}~\label{fig:rzplot_offset_300K_disordered}
+			\end{subfigure}
+	\end{subfigure}
+	\end{subfigure}
+	\begin{subfigure}{0.1\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{colorbar_jet.png}
+	\end{subfigure}	
+	\caption{Simulated X-ray diffraction patterns show some qualitative agreement with 
+	experiment. Shown is a comparison of the (a) Sandwiched, d=3.7~\AA~ (b) Sandwiched,
+	d=5~\AA~(d) Parallel Displaced, d=3.7~\AA~ and (e) Parallel Displaced, d=5~\AA~ 
+	configurations with (c) experimental WAXS. Quantitative comparisons of the relative 
+	intensities of reflections of interest are present in Table~\ref{table:relative_inensities_300K}. 
+	In all cases, R-double is not present.}~\label{fig:XRDsim} 
+  \end{figure}
+
+  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
+  R-pores appear in the expected location. R-pores is more intense than experiment, likely
+  because we are simulating a perfect, infinite hexagonal array. The real system has defects and
+  domain misalignment which decreases the overall intensity.
+  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
+  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
+  % Let's talk!
+  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
+  % pores in unit cell, tortuosity (?)
+  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
+  % effects.
+  R-spots appears to be weaker in the simulated patterns. They are also partially engulfed by
+  the wide R-$\pi$ reflection. We further explore R-spots in Section~\ref{section:rspots}.  
+  R-$\pi$ appears at a lower $q_z$ value than experiment. In all systems, the reflection 
+  reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack 
+  at least 4.2 \AA~apart rather than 3.7 \AA. This behavior is not surprising since GAFF models
+  atoms as point charges and does not appropriately model the aromatic $\pi-\pi$ interactions 
+  which would cause the monomers to stack closer together. We will explore R-$\pi$ in more detail
+  in Section~\ref{section:rpi}. R-double does not appear in any of the patterns. We will explore
+  its possible origins and reasons that it does not appear in our simulated patterns in
+  Section~\ref{section:rdouble}.
+
+  The simulated XRD pattern of the parallel displaced configuration shows an additional
+  reflection due to its helical structure. There are horizontal reflections near $|q_z|= 
+  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
+  $q_r = 0~\AA^{-1}$ so it does not appear for the same reason as R-double. This type of pattern
+  is characteristic of a helix (reference something).
+  %BJC5: reference something like a dna diffraction paper
+  It is possible that these reflections contribute to the continuation of R-double into R-
+  alkanes, as seen in the experimental pattern.
+
+  %BJC4: This paragraph might fit better before qualitative description
+  %BJC5: This could potentially supplement parts of the qualitative descriptions.
+  We quantified the numerical discrepancies present when comparing the relative intensities
+  of each reflection of interest between experimental and simulated patterns. Table 
+  ~\ref{table:relative_inensities_300K} quantifies the relative intensity of each reflection for 
+  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
+  equals 1.
+  % BJC5: above is stated in methods. Not sure if it needs to be restated.  
+  % BJC5: I need to explain how I calculated these intensities somewhere. Is this the right
+  % place to do it? I think it would just be confusing in the methods. I could also move it
+  % to supplemental.
+  % BJC5: Definitely need demonstrative figures in supporting info.
+  We measured the approximate intensity of R-$\pi$ by measuring the intensity of the peak shown
+  by the cross-section of the 2D pattern at $q_r=0$. The relative intensity of R-$\pi$ is 
+  significantly higher than experiment in our simulations. R-spots is measured as the average
+  intensity within the region bounded by a 'spot'. Spots are identified based on visual 
+  inspection. If the spots were not easily discernable, then the intensity was taken as that of
+  the intersection of R-alkanes at half the $q_z$ value of R-$\pi$, since that is where it 
+  appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
+  cases. There is no R-double intensity to be measured.
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cccccc}
+  \toprule
+ 		   & \multicolumn{5}{c}{Configuration} \\
+  \hline
+  Reflection & Experiment & Sandwiched & Parallel Displaced & Disordered Sandwiched & Disordered Parallel Displaced \\
+  \midrule
+  R-alkanes & 1.0 &  1.0 &  1.0 & 1.0 & 1.0  \\  
+  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
+  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
+  R-double  & 0.9 &  --  & --   &  -- & --   \\ 
+  \bottomrule
+  \end{tabular}
+  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
+  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
+  than experiment and R-spots reflections that are slightly lower than experiment. R-double
+  does not appear in any patterns, and thus has no measurable intensity.}
+  \label{table:relative_inensities_300K} 
+  \end{table}
+
+  There are clear differences between simulated and experimental results that must be addressed
+  and justified. We will explore the origin of each experimental reflection and form structural
+  hypotheses related to their appearance in our simulated patterns. Specifically, we want answer:  
+  \begin{enumerate}
+	\item What is the origin of R-spots?
+  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
+  	\item What is the origin of R-double?
+  \end{enumerate}
+
+% BJC5: old version
+%  Simulated XRD of the sandwiched configuration shows most all experimental features 
+%  except R-double and R-spots. R-pores and R-alkanes appear in their expected locations. 
+%  R-pores is more intense than experiment, likely because we are simulating a perfect,
+%  infinite hexagonal array. The real system has defects and domain misalignment
+%  which decreases the overall intensity. R-$\pi$ appears with very high intensity and
+%  is shifted down to a lower value of $q_z$ meaning monomers in our model prefer to 
+%  stack farther apart.   
+%
+%  Simulated XRD of the sandwiched configuration contains all experimental
+%  features except for R-double. R-alkanes, R-spots and R-pores appear close to their
+%  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
+%  a $q_z$ value lower than experiment meaning the head groups in our model prefer 
+%  to stack farther apart. 
+%
+%  Like the sandwiched configuration, the parallel displaced configuration creates
+%  a simulated XRD pattern with all major experimental reflections except for R-double.
+%  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
+%  and R-$\pi$ appear, however with a lower intensity
+%  relative to R-alkanes when compared to the sandwiched configuration. R-double
+%  appears due to the parallel displaced aromatic rings. It is a subharmonic of
+%  R-$\pi$ since the nearest vertically stacked head group to any given head group
+%  is $2\times$R-$\pi$~away. 
+%  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
+%  \begin{figure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%        \vspace{-0.2em}
+%        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{offset_rzplot.png}
+%        \caption{}~\label{fig:rz_offset}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%%        \vspace{0.25em}
+%        \includegraphics[scale=0.285]{WAXS_raw.png}
+%        \caption{}~\label{fig:raw_waxs}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%        \centering
+%        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{layered_rzplot.png}
+%        \caption{}~\label{fig:rz_layered}
+%  \end{subfigure}
+%  \begin{subfigure}{0.0544\linewidth}
+%        \centering
+%        \vspace{-4.00em}
+%        \includegraphics[width=\linewidth]{colorbar_seismic.png}
+%  \end{subfigure}
+%%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced.
 Any thoughts why?
@@
 And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
-%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
-%BJC2: Sure, I'll add that to supporting info
-  \caption{The simulated XRD pattern generated from the equilibrated trajectory
-	  of the parallel displaced configuration (a) exhibits all major reflections
-	  present in the experimental WAXS pattern (b). The simulated XRD pattern
-	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
-	  all major reflections except R-helix.}
-  \label{fig:XRDsim}
-  \end{figure}
+%%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
+%%BJC2: Sure, I'll add that to supporting info
+%  \caption{The simulated XRD pattern generated from the equilibrated trajectory
+%	  of the parallel displaced configuration (a) exhibits all major reflections
+%	  present in the experimental WAXS pattern (b). The simulated XRD pattern
+%	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
+%	  all major reflections except R-double.}
+%  \label{fig:XRDsim}
+%  \end{figure}
 
@@
 
-  In both the parallel displaced and sandwiched configurations, we noted that
-  R-$\pi$ appears in a location which corresponds to a real space separation
-  larger than experiment. We attribute this discrepancy to GAFF's inability to
-  appropriately model the aromatic interactions which would be necessary to
-  achieve the correct $\pi$-$\pi$ stacking distance. 
-  %Systems have been modeled that exhibit the correct stacking distance, however
-  %they are typically made of planar molecules spanning a large area.
-  %BJC: I saw a paper like this a long time ago, but failed to save the citation and
-  % now I am having a hard time finding it again. 
-  The monomers in our model have bulky tails whose entropic contributions compete
-  with the $\pi$-$\pi$ stacking interaction energy. There have been efforts to
-  model systems that contain $\pi$ interactions in a classical mechanical context
-  using polarizable forcefields \cite{baker_polarizable_2015},
-  %MRS6: 
-  but they are significantly more computationally expensive to
-  reach the time scales required to equilibrate these systems at the present time.
-  %MRS6: not so relevant below.
-  %We could
-  %implement a polarizable force field, however it is likely not worth the extra
-  %computational cost. If our model proves to be inadequate when simulating
-  %transport, we will revisit our current choice of forcefield.
-
-  In addition to R-$\pi$ being shifted to lower $\mathbf{q}$ values, a few
-  factors combine to make the simulated R-$\pi$ reflection visibly more intense
-  than in the experimental pattern. The simplest reason is that R-$\pi$ and
-  R-alkanes add together to boost the overall signal at interesecting values of
-  $\mathbf{q}$. In addition, we observe a much higher maximum intensity within
-  R-$\pi$. The maximum intensity within R-$\pi$ of the normalized experimental
-  pattern is 3.1, while the maximum intensity within R-$\pi$ of the normalized
-  parallel displaced simulated pattern is 32.9. 
-  %MRS2 10x is really big.
+%  In both the parallel displaced and sandwiched configurations, we noted that
+%  R-$\pi$ appears in a location which corresponds to a real space separation
+%  larger than experiment. We attribute this discrepancy to GAFF's inability to
+%  appropriately model the aromatic interactions which would be necessary to
+%  achieve the correct $\pi$-$\pi$ stacking distance. 
+%  %Systems have been modeled that exhibit the correct stacking distance, however
+%  %they are typically made of planar molecules spanning a large area.
+%  %BJC: I saw a paper like this a long time ago, but failed to save the citation and
+%  % now I am having a hard time finding it again. 
+%  The monomers in our model have bulky tails whose entropic contributions compete
+%  with the $\pi$-$\pi$ stacking interaction energy. There have been efforts to
+%  model systems that contain $\pi$ interactions in a classical mechanical context
+%  using polarizable forcefields \cite{baker_polarizable_2015},
+%  %MRS6: 
+%  but they are significantly more computationally expensive to
+%  reach the time scales required to equilibrate these systems at the present time.
+%  %MRS6: not so relevant below.
+%  %We could
+%  %implement a polarizable force field, however it is likely not worth the extra
+%  %computational cost. If our model proves to be inadequate when simulating
+%  %transport, we will revisit our current choice of forcefield.  
+%
+%  In addition to R-$\pi$ being shifted to lower $\mathbf{q}$ values, a few
+%  factors combine to make the simulated R-$\pi$ reflection visibly more intense
+%  than in the experimental pattern. The simplest reason is that R-$\pi$ and
+%  R-alkanes add together to boost the overall signal at interesecting values of
+%  $\mathbf{q}$. In addition, we observe a much higher maximum intensity within
+%  R-$\pi$. The maximum intensity within R-$\pi$ of the normalized experimental
+%  pattern is 3.1, while the maximum intensity within R-$\pi$ of the normalized
+%  parallel displaced simulated pattern is 32.9. 
+%  %MRS2 10x is really big.
 That seems hard to actually manage .
@@
 Not clear how the angle averaging obscured this before?
-  %BJC2 From plots of raw structure factor, it doesn't seem like a normalization issue. It was probably obscured in the orginal angle averaging because it 
-  % was averaged with neighboring bins
-  While direct numerical
-  comparisons between simulation and experiment aren't necessarily precise due to
-  underlying assumptions, an order of magnitude difference suggests some
-  significance. We believe that we see such a high maximum for two reasons: (1)
-  We are simulating a perfectly aligned system so all X-rays reflected along the
-  pore axis would add constructively. The crystalline domains in the real system
-  are not perfectly aligned (See azimuthal distribution in Supporting
-  Information) which would lead to an overall decrease in the intensity of
-  R-$\pi$. (2) Our system is more ordered with high correlation between layers.
-  We will come back to this point further in ensuing discussions.
-
-  There is a grid-like pattern near $\mathbf{q}=0$ which appears because the
-  simulated system shows crystalline character. The grid features along nonzero
-  values of $q_z$ line up with reflections at $q_z=0$ which indicates positional
-  correlations between columns in the z-direction. This type of correlation is
-  expected for a crystalline material. 
-%MRS6: need some justification for why we are not totally surprised the system is crystalline.
+%  %BJC2 From plots of raw structure factor, it doesn't seem like a normalization issue. It was probably obscured in the orginal angle averaging because it 
+%  % was averaged with neighboring bins
+%  While direct numerical
+%  comparisons between simulation and experiment aren't necessarily precise due to
+%  underlying assumptions, an order of magnitude difference suggests some
+%  significance. We believe that we see such a high maximum for two reasons: (1)
+%  We are simulating a perfectly aligned system so all X-rays reflected along the
+%  pore axis would add constructively. The crystalline domains in the real system
+%  are not perfectly aligned (See azimuthal distribution in Supporting
+%  Information) which would lead to an overall decrease in the intensity of
+%  R-$\pi$. (2) Our system is more ordered with high correlation between layers.
+%  We will come back to this point further in ensuing discussions.
+%
+%  There is a grid-like pattern near $\mathbf{q}=0$ which appears because the
+%  simulated system shows crystalline character. The grid features along nonzero
+%  values of $q_z$ line up with reflections at $q_z=0$ which indicates positional
+%  correlations between columns in the z-direction. This type of correlation is
+%  expected for a crystalline material. 
+%%MRS6: need some justification for why we are not totally surprised the system is crystalline.
 But is is so crystalline in the x direction?
@@
 we should talk.
-If our system met the definition of a
-  columnar liquid crystalline system, we should observe only weak short-range
-  z-directional correlation within columns, with no correlation between
-  columns\cite{chaikin_principles_1995}.
-
-  The R-spots signal, which appears in both simulated XRD patterns, is not a
-  result of alkane chain tilt. Previous literature has attributed the spots in
-  this particular WAXS pattern as the product of tilted alkane
+%If our system met the definition of a
+%  columnar liquid crystalline system, we should observe only weak short-range
+%  z-directional correlation within columns, with no correlation between
+%  columns\cite{chaikin_principles_1995}.
+
+  \subsubsection{Origin of R-spots}\label{section:rspots}
+
+  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
+  is most intense in the sandwiched configuration (Figure~\ref{fig:sandwiched280K}). The relative 
+  intensity of R-spots is higher than in experiment (1.5 vs. 1.3). R-double is still not present.  
+  We will use this configuration to more thoroughly explore the origin of R-spots.
+
+  \begin{figure}
+	  \begin{subfigure}{0.45\linewidth}
+	  	\centering
+	  	\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
+	  	\caption{}
+	  \end{subfigure}
+	  \begin{subfigure}{0.45\linewidth}
+	  	\centering
+	  	\includegraphics[width=\linewidth]{rzplot_layered_280K_jet.png}
+	  	\caption{}\label{fig:sandwiched280K}
+	  \end{subfigure}
+  \caption{R-spots increases in intensity when the temperature of the system is lowered to 280K.
+  In this case, the simulated R-spots is more intense than experiment.}
+  \end{figure}
+
+  The R-spots signal is not a result of alkane chain tilt. Previous literature
+  has attributed the spots in this particular WAXS pattern as the product of tilted alkane
   chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched
-  configuration since R-spots appears with the most strength in its simulated XRD
-  pattern. We measured the tilt angle of the alkane chains and showed that our
-  system equilibrates to an average tilt angle close to zero degrees
-  (Fig.~\ref{fig:tilt}). To understand the origin of R-spots, we determined which
+  configuration simulated at 280K. We measured the tilt angle of the alkane chains and 
+  showed that our system equilibrates to an average tilt angle close to zero degrees
+  (Fig.~\ref{fig:tilt}).
+
+   %BJC5: bootstrap this data to make it smoother.
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
+  \caption{We measured the angle made between each monomer alkane tail and the
+	  membrane plane. The average tilt angle (dashed line) is near -2\degree~which is far from 
+	  the 37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
+  \end{figure}
+
+  To understand the origin of R-spots, we determined which
   atoms gave rise to the feature. Since R-spots is present as higher intensity
@@
   the tails. By removing all non-tail atoms from the trajectory and simulating a
-  diffraction pattern, we were able to isolate the cause of the spots to the
-  tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
+  diffraction pattern with the remaining atoms, we were able to isolate the cause of 
+  the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
   the centroids of the tails and measured the angle between each centroid and its
@@
   peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
-  \caption{We measured the angle made between each monomer alkane tail and the
-	  membrane plane. The average tilt angle is near 7\degree~which is far from the
-	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
-  %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
-  %BJC2: good idea
-  \end{figure}
 
@@
 
-  The evidence supports the hypothesis that alkane chain tails pack in a
-  hexagonal array. Groups of three tails associated with each monomer prefer to
-  sit between tails of vertically stacked monomers rather than stacking directly
-  on top of them (Figure~\ref{fig:hex_tails}). This type of packing has been seen
-  before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.
+% BJC5: omit for now
+%  The evidence supports the hypothesis that alkane chain tails pack in a
+%  hexagonal array. Groups of three tails associated with each monomer prefer to
+%  sit between tails of vertically stacked monomers rather than stacking directly
+%  on top of them (Figure~\ref{fig:hex_tails}). This type of packing has been seen
+%  before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.
 
@@
         tail-only trajectory still shows R-spots}\label{fig:tails}
-        %MRS3: so I didn't realize this before, but why are there still fairly significant peaks in the pi-stacking region when the head groups are removed?
-        %Do you feel you understand this? I suppose it is because the top of the tails must be correlated with the aromatic ring by covalent bonding?
-        %BJC2: Yea, I think the reflection is correlated to the aromatic rings. The system shown is the sandwiched configuration. The intensity of "R-pi"
-        % in this pattern is lower than in the pattern generated by the full system. The aromatic rings appear to strengthen the reflection. 
-        % Also, the system is layered in the z-direction, as we show, so a reflection like that should appear. 
-        %MRS4: did you use a different scaling for the color bar here than above? If so, mention.
-        %BJC3: The scaling is the same
-        %MRS6: OK, I'm seeing this new light.
-the HUGE intensity in the simulation is from the carbon of the tail, not the pi-pi.
-There isn't anything like that in the experimental in the alkane region.
-What happens if you remove a couple of more carbons from the tails?
-Does this has something to do with the stacking of alkane tails in the z direction?
-is that not experimentally observed?
-I need to think through this a bit more .
-.
-.
-I maybe missing something obvious having to do with require correlations between the stacking of the tails and the stacking of the pi.
-Maybe normalizing by the tails is NOT the right thing to do, because in the z direction, stacked pi interactions lead to stacked tails at the same distance (a requirement of the molecules being connected, so if that stacking is different between experiment and theory, it leads to different intensities.
-On the other hand, if the experiment had tails that are stacked together at 3.7 A on average, it seems like they would have to be much flatter to fit.
-Hmmm.
-What do the aromatics signals alone look like?
-(i.e.
-the opposite of 9a).
-I need to think .
-.
-.
   \end{figure}
 
+%  \begin{figure}[!htb]
+%  \centering
+%  	\begin{subfigure}{\linewidth}
+%	\centering
+%		\begin{subfigure}{0.45\textwidth}
+%        		\centering
+%        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
+%        		\caption{}~\label{fig:offset_tails}
+%		\end{subfigure}
+%		\begin{subfigure}{0.45\textwidth}
+%		\centering
+%	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
+%		        \caption{}~\label{fig:offset_integration}
+%		\end{subfigure}
+%	\end{subfigure}
+%	\begin{subfigure}{\linewidth}
+%	\centering
+%		\begin{subfigure}{0.45\textwidth}
+%	        \centering
+%		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
+%		        \caption{}~\label{fig:layered_tails}
+%		\end{subfigure}
+%		\begin{subfigure}{0.45\textwidth}
+%        	\centering
+%		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
+%		        \caption{}~\label{fig:layered_integration}
+%		\end{subfigure}
+%	\end{subfigure} 
+%  \caption{We hypothesize that R-spots is the result of ordered tail packing.
+%	  Defining the membrane plane to be 0\degree, we measured the angles between each
+%	  alkane chain tail centroid and its nearest neighbor centroids for the
+%	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
+%	  that appear in each distribution are centered near $\pm~33\degree$. We radially
+%	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
+%	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
+%	  Peaks appear in the same location as the angle distributions which corroborates
+%	  our hypothesis. Further, we note that the peaks are strongest in both plots
+%	  associated with the sandwiched configuration. As shown in Figure
+%	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
+%	  more intense R-spots reflections. Note that plots of integrated intensity are
+%	  normalized so the average alkane intensity (excluding reflections $\pm
+%	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
+%	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
+%  \end{figure}
+
+  % BJC4: modification of above figure to only included sandwiched data. The rest can go
+  % in supporting info.
   \begin{figure}[!htb]
   \centering
-  	\begin{subfigure}{\linewidth}
-	\centering
-		\begin{subfigure}{0.45\textwidth}
-        		\centering
-        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
-        		\caption{}~\label{fig:offset_tails}
-		\end{subfigure}
-		\begin{subfigure}{0.45\textwidth}
-		\centering
-	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
-		        \caption{}~\label{fig:offset_integration}
-		\end{subfigure}
-	\end{subfigure}
 	\begin{subfigure}{\linewidth}
@@
 	  alkane chain tail centroid and its nearest neighbor centroids for the
-	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
+	  equilibrated sandwiched configuration simulated at 280K. Peaks
 	  that appear in each distribution are centered near $\pm~33\degree$. We radially
 	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
-	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
+	  configuration within the region bounding R-alkanes.
 	  Peaks appear in the same location as the angle distributions which corroborates
-	  our hypothesis. Further, we note that the peaks are strongest in both plots
-	  associated with the sandwiched configuration. As shown in Figure
-	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
-	  more intense R-spots reflections. Note that plots of integrated intensity are
-	  normalized so the average alkane intensity (excluding reflections $\pm
-	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
-	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
+	  our hypothesis.}~\label{fig:tail_packing}
   \end{figure}
@@
 %MRS6: kind of confusing with just the circles and no molecules to hang them on.
+%  \begin{figure}
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{hexagonal_tails_alt2.png} 
+%	%BJC: I can give the circle some depth if that makes it clearer
+%	\caption{Monomer tails prefer to pack in a hexagonal array. Each circle
+%		represents a monomer tail as seen if viewed by looking from the end of the tail
+%		to the pore center. Each color represents distinct monomers from adjacent
+%		layers.}~\label{fig:hex_tails}
+%  \end{figure}
+
+  There are a couple reasons why we see stronger ordered chain packing at 280 K compared to
+  experimental conditions of 300 K.
+  \begin{enumerate}
+  		\item The difference between 280K and 300K is small. Our forcefield parameters
+  		may not correctly model the behavior of the tails at 300K (citation?).
+  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
+  		If the head groups packed 3.7 \AA apart, the tails would be more confined and forced
+  		to pack between vertically adjacent monomer tails. In our case, the tail region is
+  		less dense than experiment which gives the tails freedom to organize in a more
+  		entropically favored disordered state. 
+  \end{enumerate}
+
+  \subsubsection{Discrepancies between R-$\pi$}\label{section:rpi}
+
+  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
+  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}).
+
+  %BJC5: redo after discussing with Michael
   \begin{figure}
   \centering
-	\includegraphics[width=0.5\linewidth]{hexagonal_tails_alt2.png} 
-	%BJC: I can give the circle some depth if that makes it clearer
-	\caption{Monomer tails prefer to pack in a hexagonal array. Each circle
-		represents a monomer tail as seen if viewed by looking from the end of the tail
-		to the pore center. Each color represents distinct monomers from adjacent
-		layers.}~\label{fig:hex_tails}
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
+  \caption{}\label{fig:z_correlation_sandwich}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_offset.png}
+  \caption{}\label{fig:z_correlation_offset}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  %BJC4: This is noisier than l=3.7 angstrom, but I can still pick out peaks. I'm unsure
+  % how to quantify the difference. The correlation length is very similar to the more
+  % ordered configuration.
+  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
+  \caption{}\label{fig:z_correlation_sandwich_disordered}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  %BJC4: There really aren't any good peaks here. 
+  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
+  \caption{}\label{fig:z_correlation_offset_disordered}
+  \end{subfigure}  
+  \caption{}\label{fig:correlation}
   \end{figure}
 
-  \subsubsection{Layer partitioning}
-
-%MRS6: should probably be present tense.  Maybe phrase ``in our simulations, layers are'' 
-  In our simulations, layers are well-defined and persistent, answering question
-  (\ref{point:layers}). We established our conclusion by plotting the two
-  dimensional pair distribution function, $g(y,z)$ of head group phenyl rings
-  using Equation~\ref{eqn:correlation} (Figure \ref{fig:yz_correlation}). In both
-  configurations, the phenyl rings stack in the z-direction, along $y=0$, and
-  clear layers are formed. The layers in the sandwiched configuration are more
-  defined than those in the parallel displaced configuration and are strongly
-  correlated with adjacent layers. We also observe correlation of layers between
-  pores indicated by the non uniformity in $g(y,z)$ in adjacent columns (along $y
-  = \pm 3.65$). Parallel displaced layers display weaker correlations but do not
-  decay in their intensity as z increases. We do not see correlation between
-%MRS6: correlations of what between pores?
-  pores, however correlations within pores are strong throughout the length of
-  the unit cell since there is no noticeable decay in layer intensity.
+  %BJC5: conclusions here will need modification
+  The correlation length between stacked monomer head groups shows the best agreement with
+  experimental for systems simulated in the ordered basin.
+  %BJC4: explanation of correlation function calculation in methods section. 
+  %MRS5: the correlation length doesn't look like that great a fit, since it misses the first point by so much.  We may need to reevaluate a litle how this is done. 
+  %BJC5: forgot an amplitude on exponential fit. New results show lower correlation length
+  We calculated correlation length by fitting a decaying exponential function to all peaks of
+  $g(z)$ for the sandwiched configuration and to every other peak of $g(z)$ for the parallel
+  displaced configuration. The correlation length of systems simulated in the ordered basin are
+  11.2 \AA and 14.9 \AA	for the parallel displaced and sandwiched configurations respectively. 
+  %BJC5: Something about disordered systems.
+  Systems simulated in the ordered basin show correlation closest to the experimental correlation
+  length of 10.1 \AA. They are still slightly more correlated than experiment which would lead to
+  an increase in constructive X-ray scattering. 
+  %BJC5: this statement might not be true anymore.
+
+  Additionally, our system models near-perfectly straight pores with no defects which will
+  lead to higher intensity vertical stacking reflections. Nearly all of the intensity in R-$\pi$
+  of our simulated patterns is concentrated at a single point. Figure ~\ref{fig:intense_rpi}
+  shows the same simulated patterns with the upper boundary on the colorbar adjusted to be 6x
+  higher. The only distinguishable reflections are those of R-$\pi$ and R-pores. In the 
+  experimental pattern, the intensity is more evenly spread out over all of R-$\pi$.
 
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{layered_yz_correlation.png}
-	\caption{}\label{fig:layered_yz_correlation}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{offset_yz_correlation.png}
-        \caption{}\label{fig:offset_yz_correlation}
-  \end{subfigure}
-  %MRS6: have the same color scale in both figures to compare them?
-  \caption{2D pair distribution functions generated from systems built in the 
-	   sandwiched (a) and parallel displaced (b) configurations, provide
-           a more detailed picture of the pore structure in each. The sandwiched
-	   configuration}\label{fig:yz_correlation}
-%MRS6: caption not finished?
+  \includegraphics[width=0.4\textwidth]{sandwich_rzplot_highlimit_cbar.png}
+  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections. Here, the 
+  colorbar was scaled so that the max is 6x higher than all other plots.}\label{fig:intense_rpi}
+  % BJC5: could benefit from an adjusted colorbar experimental pattern.
   \end{figure}
 
-  We plotted the one-dimensional pair distribution function, $g(z)$, for the
-  phenyl rings and for carbon atoms that make up the monomer tails (Figure
-  \ref{fig:zdf}). The plots show clear periodic maxima where layers are present.
-  Layering is most pronounced in the head group region, however there is still a
-  degree of layering that persists into the tail region. Using a Fourier
-  transform on $g(z)$ from the head groups, we see that sandwiched configuration
-  layers stack 4.39 \AA~apart while parallel displaced configuration layers stack
-  4.38 \AA~apart. Both stacking distances are in agreement with those observed
-  in the simulated XRD patterns.
-
-  %MRS6: do you need both the 2D and 1D correlation functions?
-  \begin{figure}
-        \centering
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
-                \caption{}\label{fig:zdf_layered}
-        \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
-                \caption{}\label{fig:zdf_offset}
-        \end{subfigure}
-	\caption{We support the existence of layers with the observance of
-		clear periodic maxima in the $z$-direction pair distribution functions of the
-		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
-		displaced configurations. The extent to which we consider a system to be
-		layered is based on the magnitude of the deviation of the periodic maxima from
-		the average number density. The sandwiched configuration possesses a higher
-		degree of layering than the parallel displaced configuration and, in both
-		cases, the head group region has a higher degree of layer partitioning than the
-		tail region. (See Supporting information for detailed definitions of the head
-		group and tail regions)}\label{fig:zdf}
-  \end{figure}
-
-  \subsubsection{Initial Layer Spacing Affects System Equilibration}
-
-  All systems up to this point were built with layers stacked 3.7 \AA~apart.
-  When we build systems with layers stacked 5.0 \AA~apart and then let them
-  equilibrate, we observe long-term stability of a qualitatively different
-  configuration, suggesting that we have found another metastable free energy
-  basin, further corroborating question (\ref{point:metastable}). 
-  %The basins are
-  %differentiated by their relative degrees of ordering resulting from different
-  %spatial arrangements. 
-  For reasons we will develop in the next segment of our
-  discussion, configurations intially built with layers stacked 5.0 \AA~apart 
-  will be grouped into the disordered pore basin, while those built with layers
-  initially stacked 3.7 \AA~apart will be grouped into the ordered pore basin.
-
-  The equilibrated pore spacing and distance between layers are different in
-  the disordered pore basin. For both head group stacking arrangements, we
-  observe an increase in the equilibrated distance between layers
-  (Fig.~\ref{fig:dbwl_disordered}) and a corresponding decrease in pore spacing
-  (Fig.~\ref{fig:p2p_disordered}).
-
-  The simulated X-ray diffraction patterns indicate further structural
-  differences. In the parallel displaced configuration, almost all contrast
-  between R-spots and R-alkanes fades (Figure~\ref{fig:offset_disordered_xrd}).
-  In the sandwiched configuration, R-spots is present, but there are only two
-  spots located at the intersection of $q_z=0$ with R-alkanes.
-  (Figure~\ref{fig:layered_disordered_xrd}).
-
-% BJC: in the interest of being concise, I leave this out for now.
-%  The sandwiched and parallel displaced assemblies do not deviate from their
-%  initial head group arrangement. R-helix is still faintly visible in the
-%  parallel displaced configuration and is absent in the sandwiched simulated
-%  diffraction pattern. The spectroscopic signatures are unique to the two
-%  different head group configurations.
-
-  \begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{dbwl.png}
-                \caption{}~\label{fig:dbwl_disordered}
-        \end{subfigure}%
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{p2p2.png}
-                \caption{}~\label{fig:p2p_disordered}
-        \end{subfigure}
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{disorder_offset_rzplot.png}
-                \caption{}~\label{fig:offset_disordered_xrd}
-        \end{subfigure}%
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{disorder_rzplot.png}
-                \caption{}~\label{fig:layered_disordered_xrd}
-        \end{subfigure}
-	\caption{There are distinct differences between the disordered and ordered pore systems. 
-		When layers are initially stacked 5\AA~ apart, the distance
-		between layers increases (a) and the pore spacing decreases (b) in comparison to
-		the ordered pore systems. The simulated
-		XRD patterns of disordered pore systems are also appreciably different, most 
-		notably in the region bounded by R-alkanes. The disordered pore
-		systems started in the parallel displaced configuariton (c) does not show R-spots
-		or R-$\pi$ which suggests that head groups are not associating with each other
-		and tails are distributed nearly isotropically. The disordered pore system
-		started in the sandwiched configuration (d) does not show R-$\pi$ but R-spots 
-		is present in different locations because the tails are packed in a different
-		motif.}
-  \end{figure}
-
-  %BJC: this may belong in methods, but I think it might fit here because it
-  % gives context for the choice of functional form to fit
-
-  We quantified order in the z-direction by measuring the correlation lengths
-  of all configurations. We measured the correlation length, L, by fitting $g(z)$
-  using a non-linear least squares algorithm subject to a function of the form:
-  \begin{equation}
-  	1 + Asin(Bx + C)e^{-z/L}
-        \label{eqn:correlation_fit}
-  \end{equation}
-  where z is the independent variable and all other variables are fitting
-  parameters. The correlation length for each system is given in
-  Table~\ref{table:nematic}.
-
-  Correlation lengths are shorter in the disordered pore basin than in the
-  ordered pore basin. Layers in the ordered pore basin are strongly correlated
-  with neighboring layers up to more than 10 layers away. This behavior deviates
-  from experimental evidence. The experimental correlation length (See
-  Suppporting Information for details its derivation) suggests that layers are
-  correlated with about 3 neighboring layers which is closer to the values
-  exhibited by the disordered pore basin. We may need to simulate a system with
-  many more layers in order to reduce the correlation contributed by periodic
-  copies of the system.
-
-%MRS6: not sure if we WANT to do this, but could do a simulation with 2x as many layers and see if the correlation changes.
-%BJC2: have one that is 3x going right now
-
-  We calculated the nematic order parameter for each system using Equation
-  \ref{eqn:nematic_order_parameter}. The calculated values of S are presented in
-  Table \ref{table:nematic}. The full distributions of angles between director
-  \textbf{n} and vectors orthogonal to monomer phenyl rings are presented in the
-  Supporting Information. In general, ordered pore basin systems are more
-  nematically ordered than disordered pore basin systems and sandwiched
-  configuration systems are more nematically ordered than parallel displaced
-  configuration systems. The head groups of the disordered pore basin have more
-  rotational freedom about the xy plane likely due to the larger separation
-  between layers. Similarly, monomers situated in the sandwiched configuration
-  are constrained by other monomers stacked directly above and below them, while
-  monomers in the parallel displaced configuration have no direct neighbors
-  vertically which provides them with more rotational freedom.
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{ccc}
-  \toprule
-  System & Correlation Length (\AA) & Nematic Order Parameter (S) \\
-  \midrule
-  Sandwiched, Ordered & 41 $\pm$ 3 & 0.659 $\pm$ 0.003 \\
-  Parallel Displaced, Ordered & 86 $\pm$ 14 & 0.601 $\pm$ 0.003 \\
-  Sandwiched, Disordered & 17 $\pm$ 3 & 0.565 $\pm$ 0.002 \\
-  Parallel Displaced, Disordered & 9 $\pm$ 1 & 0.503 $\pm$ 0.002 \\
-  Experiment & 10 $\pm$ 1 & -- \\
-  \bottomrule
-  \end{tabular}
-  \caption{The nematic order parameter, S, is higher when layers are initially spaced
-  3.7 \AA apart. In general, the sandwiched configuration has higher nematic order
-  than the parallel displaced configuration. Correlation lengths are higher in
-  the ordered pore basin. Correlation lengths in the disordered pore basin are
-  in closer agreement with experiment. WHY IS THIS BOLD??!}~\label{table:nematic}
-%MRS6: for some reason, might be set in the jpcbfk package?
-  \end{table}
+% BJC5: this is no longer a section after reorganization
+%  \subsubsection{Layer partitioning}
+%
+%  In our simulations, layers are well-defined and persistent, answering question
+%  (\ref{point:layers}). We established our conclusion by plotting the two
+%  dimensional pair distribution function, $g(y,z)$ of head group phenyl rings
+%  using Equation~\ref{eqn:correlation} (Figure \ref{fig:yz_correlation}). In both
+%  configurations, the phenyl rings stack in the z-direction, along $y=0$, and
+%  clear layers are formed. The layers in the sandwiched configuration are more
+%  defined than those in the parallel displaced configuration and are strongly
+%  correlated with adjacent layers. We also observe correlation of layers between
+%  pores indicated by the non uniformity in $g(y,z)$ in adjacent columns (along $y
+%  = \pm 3.65$). Parallel displaced layers display weaker correlations but do not
+%  decay in their intensity as z increases. We do not see correlation between
+%%MRS6: correlations of what between pores?
+%  pores, however correlations within pores are strong throughout the length of
+%  the unit cell since there is no noticeable decay in layer intensity. 
+%
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%	\centering
+%	\includegraphics[width=\textwidth]{layered_yz_correlation.png}
+%	\caption{}\label{fig:layered_yz_correlation}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%        \centering
+%        \includegraphics[width=\textwidth]{offset_yz_correlation.png}
+%        \caption{}\label{fig:offset_yz_correlation}
+%  \end{subfigure}
+%  %MRS6: have the same color scale in both figures to compare them?
+%  \caption{2D pair distribution functions generated from systems built in the 
+%	   sandwiched (a) and parallel displaced (b) configurations, provide
+%           a more detailed picture of the pore structure in each. The sandwiched
+%	   configuration}\label{fig:yz_correlation}
+%%MRS6: caption not finished?
+%  \end{figure} 
+%
+%  We plotted the one-dimensional pair distribution function, $g(z)$, for the
+%  phenyl rings and for carbon atoms that make up the monomer tails (Figure
+%  \ref{fig:zdf}). The plots show clear periodic maxima where layers are present.
+%  Layering is most pronounced in the head group region, however there is still a
+%  degree of layering that persists into the tail region. Using a Fourier
+%  transform on $g(z)$ from the head groups, we see that sandwiched configuration
+%  layers stack 4.39 \AA~apart while parallel displaced configuration layers stack
+%  4.38 \AA~apart. Both stacking distances are in agreement with those observed
+%  in the simulated XRD patterns.
+%
+%  %MRS6: do you need both the 2D and 1D correlation functions?
+%  \begin{figure}
+%        \centering
+%        \begin{subfigure}{0.45\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
+%                \caption{}\label{fig:zdf_layered}
+%        \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
+%                \caption{}\label{fig:zdf_offset}
+%        \end{subfigure}
+%	\caption{We support the existence of layers with the observance of
+%		clear periodic maxima in the $z$-direction pair distribution functions of the
+%		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
+%		displaced configurations. The extent to which we consider a system to be
+%		layered is based on the magnitude of the deviation of the periodic maxima from
+%		the average number density. The sandwiched configuration possesses a higher
+%		degree of layering than the parallel displaced configuration and, in both
+%		cases, the head group region has a higher degree of layer partitioning than the
+%		tail region. (See Supporting information for detailed definitions of the head
+%		group and tail regions)}\label{fig:zdf}
+%  \end{figure}
+
+%  \subsubsection{Initial Layer Spacing Affects System Equilibration}
+%
+%  All systems up to this point were built with layers stacked 3.7 \AA~apart.
+%  When we build systems with layers stacked 5.0 \AA~apart and then let them
+%  equilibrate, we observe long-term stability of a qualitatively different
+%  configuration, suggesting that we have found another metastable free energy
+%  basin, further corroborating question (\ref{point:metastable}). 
+%  %The basins are
+%  %differentiated by their relative degrees of ordering resulting from different
+%  %spatial arrangements. 
+%  For reasons we will develop in the next segment of our
+%  discussion, configurations intially built with layers stacked 5.0 \AA~apart 
+%  will be grouped into the disordered pore basin, while those built with layers
+%  initially stacked 3.7 \AA~apart will be grouped into the ordered pore basin.
+%
+%  The equilibrated pore spacing and distance between layers are different in
+%  the disordered pore basin. For both head group stacking arrangements, we
+%  observe an increase in the equilibrated distance between layers
+%  (Fig.~\ref{fig:dbwl_disordered}) and a corresponding decrease in pore spacing
+%  (Fig.~\ref{fig:p2p_disordered}).
+%
+%  The simulated X-ray diffraction patterns indicate further structural
+%  differences. In the parallel displaced configuration, almost all contrast
+%  between R-spots and R-alkanes fades (Figure~\ref{fig:offset_disordered_xrd}).
+%  In the sandwiched configuration, R-spots is present, but there are only two
+%  spots located at the intersection of $q_z=0$ with R-alkanes.
+%  (Figure~\ref{fig:layered_disordered_xrd}). 
+%
+%% BJC: in the interest of being concise, I leave this out for now.
+%%  The sandwiched and parallel displaced assemblies do not deviate from their
+%%  initial head group arrangement. R-double is still faintly visible in the
+%%  parallel displaced configuration and is absent in the sandwiched simulated
+%%  diffraction pattern. The spectroscopic signatures are unique to the two
+%%  different head group configurations.
+%
+%  \begin{figure}[!hbt]
+%        \centering
+%        \begin{subfigure}{0.45\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth]{dbwl.png}
+%                \caption{}~\label{fig:dbwl_disordered}
+%        \end{subfigure}%
+%        \begin{subfigure}{0.45\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth]{p2p2.png}
+%                \caption{}~\label{fig:p2p_disordered}
+%        \end{subfigure}
+%        \begin{subfigure}{0.45\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth]{disorder_offset_rzplot.png}
+%                \caption{}~\label{fig:offset_disordered_xrd}
+%        \end{subfigure}%
+%        \begin{subfigure}{0.45\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth]{disorder_rzplot.png}
+%                \caption{}~\label{fig:layered_disordered_xrd}
+%        \end{subfigure}
+%	\caption{There are distinct differences between the disordered and ordered pore systems. 
+%		When layers are initially stacked 5\AA~ apart, the distance
+%		between layers increases (a) and the pore spacing decreases (b) in comparison to
+%		the ordered pore systems. The simulated
+%		XRD patterns of disordered pore systems are also appreciably different, most 
+%		notably in the region bounded by R-alkanes. The disordered pore
+%		systems started in the parallel displaced configuariton (c) does not show R-spots
+%		or R-$\pi$ which suggests that head groups are not associating with each other
+%		and tails are distributed nearly isotropically. The disordered pore system
+%		started in the sandwiched configuration (d) does not show R-$\pi$ but R-spots 
+%		is present in different locations because the tails are packed in a different
+%		motif.}
+%  \end{figure}
+%
+%  %BJC: this may belong in methods, but I think it might fit here because it
+%  % gives context for the choice of functional form to fit
+%
+%  We quantified order in the z-direction by measuring the correlation lengths
+%  of all configurations. We measured the correlation length, L, by fitting $g(z)$
+%  using a non-linear least squares algorithm subject to a function of the form:
+%  \begin{equation}
+%  	1 + Asin(Bx + C)e^{-z/L}
+%        \label{eqn:correlation_fit}
+%  \end{equation}
+%  where z is the independent variable and all other variables are fitting
+%  parameters. The correlation length for each system is given in
+%  Table~\ref{table:nematic}.
+%
+%  Correlation lengths are shorter in the disordered pore basin than in the
+%  ordered pore basin. Layers in the ordered pore basin are strongly correlated
+%  with neighboring layers up to more than 10 layers away. This behavior deviates
+%  from experimental evidence. The experimental correlation length (See
+%  Suppporting Information for details its derivation) suggests that layers are
+%  correlated with about 3 neighboring layers which is closer to the values
+%  exhibited by the disordered pore basin. We may need to simulate a system with
+%  many more layers in order to reduce the correlation contributed by periodic
+%  copies of the system. 
+%
+%%MRS6: not sure if we WANT to do this, but could do a simulation with 2x as many layers and see if the correlation changes.
+%%BJC2: have one that is 3x going right now
+%
+%  We calculated the nematic order parameter for each system using Equation
+%  \ref{eqn:nematic_order_parameter}. The calculated values of S are presented in
+%  Table \ref{table:nematic}. The full distributions of angles between director
+%  \textbf{n} and vectors orthogonal to monomer phenyl rings are presented in the
+%  Supporting Information. In general, ordered pore basin systems are more
+%  nematically ordered than disordered pore basin systems and sandwiched
+%  configuration systems are more nematically ordered than parallel displaced
+%  configuration systems. The head groups of the disordered pore basin have more
+%  rotational freedom about the xy plane likely due to the larger separation
+%  between layers. Similarly, monomers situated in the sandwiched configuration
+%  are constrained by other monomers stacked directly above and below them, while
+%  monomers in the parallel displaced configuration have no direct neighbors
+%  vertically which provides them with more rotational freedom. 
+%
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{ccc}
+%  \toprule
+%  System & Correlation Length (\AA) & Nematic Order Parameter (S) \\
+%  \midrule
+%  Sandwiched, Ordered & 41 $\pm$ 3 & 0.659 $\pm$ 0.003 \\
+%  Parallel Displaced, Ordered & 86 $\pm$ 14 & 0.601 $\pm$ 0.003 \\
+%  Sandwiched, Disordered & 17 $\pm$ 3 & 0.565 $\pm$ 0.002 \\
+%  Parallel Displaced, Disordered & 9 $\pm$ 1 & 0.503 $\pm$ 0.002 \\
+%  Experiment & 10 $\pm$ 1 & -- \\
+%  \bottomrule
+%  \end{tabular}
+%  \caption{The nematic order parameter, S, is higher when layers are initially spaced
+%  3.7 \AA apart. In general, the sandwiched configuration has higher nematic order
+%  than the parallel displaced configuration. Correlation lengths are higher in
+%  the ordered pore basin. Correlation lengths in the disordered pore basin are
+%  in closer agreement with experiment. WHY IS THIS BOLD??!}~\label{table:nematic}
+%%MRS6: for some reason, might be set in the jpcbfk package?
+%  \end{table}
 
@@
 
-  %BJC: this might be better situated before the numerical calculations that go 
-  %into Table 1
-  We observe evidence of disorder in the xy plane of the disordered pore basin when
-  we plot the two dimensional pair distribution function, $g(x,y)$, between the
-  centers of mass of monomer phenyl rings (Figure \ref{fig:xy_correlation}). The
-  difference is most apparent in the plots of the sandwiched configurations. In
-  the ordered pore basin, head groups primarily stay stacked on top of each other
-  while in the disordered pore basin, head groups exhibit more motion about the pore
-  center and even drift into the middle of the pore. $g(x,y)$ for the parallel displaced
-  configuration is less informative since adjacent layers are displaced in a way that
-  occupies the gaps that are seen in $g(x,y)$ for the sandwiched configuration
-
-  \begin{figure}
-  \begin{subfigure}{1\linewidth}
-        \centering
-        \begin{subfigure}{0.47\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{layered_xy_correlation.png}
-                \caption{Sandwiched, Ordered Pore Basin}~\label{fig:sandwich_xy}
-        \end{subfigure}
-        \begin{subfigure}{0.47\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{disorder_xy_correlation.png}
-                \caption{Sandwiched, Disordered Pore Basin}~\label{fig:disorder_sandwich_xy_correlation}
-       \end{subfigure}
-       \begin{subfigure}{0.47\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{offset_xy_correlation.png}
-                \caption{Parallel Displaced, Ordered Pore Basin}~\label{fig:offset_xy}
-        \end{subfigure}
-        \begin{subfigure}{0.47\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{disorder_offset_xy_correlation.png}
-                \caption{Parallel Displaced, Disordered Pore Basin}~\label{fig:disorder_offset_xy_correlation}
-        \end{subfigure}
-  \end{subfigure}
-  \caption{$g(x,y)$ for sandwiched and parallel displaced configurations in the
-	  ordered and disordered pore basins illustrates the increase in xy plane
-	  disorder when initial configuration layer stacking distance is increase from
-	  3.7 \AA~to 5 \AA~apart.}\label{fig:xy_correlation}
+%  %BJC: this might be better situated before the numerical calculations that go 
+%  %into Table 1
+%  We observe evidence of disorder in the xy plane of the disordered pore basin when
+%  we plot the two dimensional pair distribution function, $g(x,y)$, between the
+%  centers of mass of monomer phenyl rings (Figure \ref{fig:xy_correlation}). The
+%  difference is most apparent in the plots of the sandwiched configurations. In
+%  the ordered pore basin, head groups primarily stay stacked on top of each other
+%  while in the disordered pore basin, head groups exhibit more motion about the pore
+%  center and even drift into the middle of the pore. $g(x,y)$ for the parallel displaced
+%  configuration is less informative since adjacent layers are displaced in a way that
+%  occupies the gaps that are seen in $g(x,y)$ for the sandwiched configuration 
+%
+%  \begin{figure}
+%  \begin{subfigure}{1\linewidth}
+%        \centering
+%        \begin{subfigure}{0.47\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth]{layered_xy_correlation.png}
+%                \caption{Sandwiched, Ordered Pore Basin}~\label{fig:sandwich_xy}
+%        \end{subfigure}
+%        \begin{subfigure}{0.47\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth]{disorder_xy_correlation.png}
+%                \caption{Sandwiched, Disordered Pore Basin}~\label{fig:disorder_sandwich_xy_correlation}
+%       \end{subfigure}
+%       \begin{subfigure}{0.47\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth]{offset_xy_correlation.png}
+%                \caption{Parallel Displaced, Ordered Pore Basin}~\label{fig:offset_xy}
+%        \end{subfigure}
+%        \begin{subfigure}{0.47\linewidth}
+%                \centering
+%                \includegraphics[width=\linewidth]{disorder_offset_xy_correlation.png}
+%                \caption{Parallel Displaced, Disordered Pore Basin}~\label{fig:disorder_offset_xy_correlation}
+%        \end{subfigure}
+%  \end{subfigure}
+%  \caption{$g(x,y)$ for sandwiched and parallel displaced configurations in the
+%	  ordered and disordered pore basins illustrates the increase in xy plane
+%	  disorder when initial configuration layer stacking distance is increase from
+%	  3.7 \AA~to 5 \AA~apart.}\label{fig:xy_correlation}
+%  \end{figure}
+
+  \subsubsection{Origin of R-double}\label{section:rdouble}
+
+  There is no way to produce R-double without a more complex initial configuration. We 
+  calculated the structure factor of simple systems that mimic the parallel
+  displaced and sandwiched configurations. Neither give rise to R-double. (See Figure "fourier
+  transforms of simple systems" in supporting info). The appearance of R-double implies a
+  vertical modulation in electron density every 7.4 \AA. It is possible that this modulation 
+  occurs in either the head or the tails. There is a not a unique solution to this problem,
+  however we can speculate based on what makes the most physical sense.
+
+  We can produce R-double if our initial configuration contains alternating parallel and
+  antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
+  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). It is difficult to physically
+  justify this system. Systems built this way are only stable if position restraints are placed
+  on all head group heavy atoms. Carboxylate groups quickly revert to the parallel position as 
+  restraints are released. There is an appreciable energy barrier that prevents rotation
+  of carboxylate groups attached to phenyl rings since the group extends the system's 
+  $\pi$ conjugation. (citation) (See figure in supporting info with energy barrier plots)
+  %BJC5: add citation for extended pi conjugation
+  %BJC5: add figure reference and figure to supporting info
+  There are instances where carboxylate groups in other systems rotate out of plane. Bushey et
+  al. showed that bulky carbonyl-containing substituents of stacked arene molecules tended to
+  tilt 45$\degree$ in order to relieve steric strain, thus allowing $\pi$-stacking between 
+  molecules, and to hydrogen bond with neighboring molecules. Lorenzo and Gra\~{n}a found 3
+  stable dimers of gallic acid (from which the monomer, Na-GA3C11 is derived) with adenine. In
+  all cases, the carboxylate group remained planar, even with evidence of hydrogen bonding
+  between the carboxyl group and nitrogen atoms of adenine. The monomers which we are studying
+  have no opportunities to hydrogen bond and are confined so that any rotation about the phenyl--
+  carboxylate bond would be sterically hindered.
+
+  We can also produce R-double if layers are not uniformly spaced. Rather, monomers might form 
+  pairs that stack less than 3.7~\AA~apart, and whose center of masses are spaced 7.4 \AA 
+  from the next pair of monomers (Figure ~\ref{fig:staggered_rzplot_norestraints}). To our 
+  knowledge, there have been no studies that specifically address the possibility of a
+  configuration like this. Our forcefield causes our system to tend towards uniformly spaced
+  layers. As expected, simulations of this type of system are only stable if position restraints
+  are applied to heavy atoms of the phenyl rings.
+
+  Our final hypothesized configuration which produces R-double focuses on the orientation of the
+  tails. In this configuration, monomers are rotated so that the vector created by the  
+  bond extending from the carboxylate carbon to the phenyl ring is oriented $\pm 15 \degree$
+  with respect to the vector extending from the carboxylate carbon to the pore	center (Figure
+  ~\ref{fig:rotated_monomers_rzplot_norestraints}). Every other monomer layer is rotated $+15
+  \degree$ and those in between are rotated $-15 \degree$. This configuration allows monomer
+  tails to sit between adjacent monomer tails which may be the most favorable way for them to
+  pack. This configuration is stable short-term while unrestrained however R-double quickly 
+  fades after a few nanoseconds of simulation. Still, this may be the most reasonable
+  explanation for the appearance of R-double. The long-term stability of a configuration
+  similar to this may be feasible if monomers stay stacked 3.7 \AA apart.
+
+  \begin{figure}[htb]
+  \centering
+  %BJC4: I could cut out the tails in the three real space configurations
+  %BJC4: I can remove some of the colorbars and state that they all follow the same color bar. 
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
+	\label{fig:rotated_carboxylate}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{staggered.png}
+	\label{fig:staggered}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers.png}
+  	\label{fig:rotated_monomers}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
+  	\label{fig:rotated_carboxylate_rzplot_restrained}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.png}
+  	\label{fig:staggered_rzplot_restrained}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
+  	\label{fig:rotated_monomers_rzplot_restrained}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
+  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
+  	%BJC4: needs to run longer
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png}
+  	\caption{}\label{fig:staggered_rzplot_norestraints}
+  	%BJC4: needs to be done
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
+  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
+  \end{subfigure}
+  \caption{R-double is present in all three inital configurations tested while the heavy atoms
+  in the headgroup are held in place with position restraints. R-double fades once 
+  the position restriants are released.}\label{fig:rdouble}
+%MRS5: the conclusion seems like it actually may be ``this doesn't work either''.  How do they line up? Do they go to either parallel displaced or sandwiched?
   \end{figure}
 
+% BJC5 : Matt wants  a section like this somewhere.
   \subsection{Slow dynamics}
-%MRS6: Is the fact that it's lyotropic relevant? 
+
   We observe unusually slow dynamics in our system. Typical diffusion constants
@@
   $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
-  constants of monomers in each of the systems we studied (Table~\ref{table:msd})
-  and learned that they are all on the order of $10^{-14}~m^2/s$. Our systems may
-  be frozen in a glassy state. It is also possible that we are simply observing
-  characteristics of the experimental system. There has been no experimental work
-  done to study diffusion of NA-GA3C11 monomers in the Col\textsubscript{h}
+  constants of monomers in each of the systems we studied (See Table~\ref{S-table:msd}
+  in Supporting Information) and learned that they are all on the order of $10^{-14}~m^2/s$.
+  Our systems may be frozen in a glassy state. It is also possible that we are simply 
+  observing characteristics of the experimental system. There has been no experimental work
+  done to study diffusion of Na-GA3C11 monomers in the Col\textsubscript{h}
   system and no measurement of the glass transition temperature. Such a low
@@
 %MRS6: I don't know that the equilibration procedure induces it; I doubt a metastable state would have slower kinetics than the real state. It might be the force field is too stable. 
-  It is possible that our equilibration procedure may induce glassy phase
-  configurations. We have already shown that our system has some dependence on
-  initial configuration. It is conceivable that after a fast initial relaxation,
-  the system gets locked into a structure close to its initial configuration.
-  The glassy state of these systems may be the reason we observe such high
-  correlation lengths in the ordered pore basin systems.  Unfortunately, we are
-  unable to resolve the exact atomistic structure using existing experimental
-  techniques, so we are left to find out which initial configuration results in a
-  model with the closest match to experimental data.
-%MRS6: don't need a table if all the same.
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{cc}
-  \toprule
-  System & Diffusion Constant ($m^2/s$) \\ 
-  \midrule
-  Sandwiched, Ordered & $10^{-14}$ \\
-  Parallel Displaced, Ordered & $10^{-14}$ \\
-  Sandwiched, Disordered & $10^{-14}$ \\
-  Parallel Displaced, Disordered & $10^{-14}$ \\
-  \bottomrule
-  \end{tabular}
-  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
-  which is three orders of magnitude lower than literature values.}~\label{table:msd}
-  \end{table}
-
-  \subsubsection{Chemical composition of pore columns}
-
-%MRS: I think you will need to refer back to names of the questions (or at least shortened versions of the names): people skimming the paper will not remember what the numbers are.
-  In order to address question (\ref{point:poredefinition}), we plotted the
-  number densities of heavy atoms in the head group, carbon atoms in the tail
+%  It is possible that our equilibration procedure may induce glassy phase
+%  configurations. We have already shown that our system has some dependence on
+%  initial configuration. It is conceivable that after a fast initial relaxation,
+%  the system gets locked into a structure close to its initial configuration.
+%  The glassy state of these systems may be the reason we observe such high
+%  correlation lengths in the ordered pore basin systems. Unfortunately, we are
+%  unable to resolve the exact atomistic structure using existing experimental
+%  techniques, so we are left to find out which initial configuration results in a
+%  model with the closest match to experimental data.
+
+  There is not enough movement on the timescales we simulated for the system to 
+  consistently reach a structure equivalent to experiment. In all cases our monomers
+  equilibrate to a stacking distance that is too large compared to experiment. 
+  While this may be in large part due to the forcefield's inability to model aromatic
+  interactions, it is also possible that the monomer tails do not pack as tightly as 
+  they could. More densely packed tails could allow the monomers to stack closer 
+  together.
+
+  We quantified the movement of the tails during our simulations by calculating the 
+  autocorrelation function of the dihedral angle formed around the bond between the 
+  head groups and the ether oxygens which attach the tails to the head group. 
+  %BJC5: add diagram of which oxygens I'm talking about to the supporting info.
+  We exclude the dihedral from the middle tail since it is fundamentally different
+  than the two symmetric outside tails.
+
+  The ether dihedrals become decorrelated on a reasonable timescale when the temperature
+  is raised. At 300K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
+  not cross the x-axis until $\approx$ 105 ns meaning that tails might only fully rotate
+  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
+  function plateau's near a value of -0.2 which indicates that the tails are starting in 
+  an unfavorable configuration. We implemented distance restraints between the centers of 
+  mass of monomer head groups to preserve the hexagonal phase (see Supporting Information
+  %BJC5: supporting info section on this doesn't exist yet.
+  for further detail), then rose the temperature of the equilibrated 300 K system to 500 K.
+  We witnessed decorrelation of tails after $\approx$ 11 ns with a plateau at 0, 
+  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed the 
+  resultant configuration back down to 300 K to see if the increased rotational freedom 
+  might allow the system to relax into to a more tightly packed configuration.
+  %BJC5: more to come.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.png}
+  	\caption{300K}\label{fig:dihedrals_300K}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.png}
+  	\caption{300K}\label{fig:dihedrals_500K}
+  \end{subfigure}
+  \caption{}\label{fig:dihedrals}
+  \end{figure}
+
+  \subsection{Chemical composition of pore columns}
+
+%MRS5: put a little more of the rational for looking at this here. Why should they care?
+  We plotted the number densities of heavy atoms in the head group, carbon atoms in the tail
   region and all sodium ions (Figure~\ref{fig:densities}). For the head group
@@
 
+  In general, the composition of the pores is similar between all systems. We believe we can
+  study transport in any of the systems presented here and still extract valuable information.
+  We will need to verify that this assumption is true.
+
+  %BJC5: redo the numbers in this section.
   In all cases, the space in the pore region is filled with sodium ions and
@@
 
+% BJC5 : Move this figure to supporting
   \begin{figure}
@@
 
+%BJC5 : play with color scheme to make this viable
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{sodium_density.png}
+        \caption{Sodium Ions}
+        \label{fig:sodium_regional_density}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{head_group_density.png}
+        \caption{Head Groups}
+        \label{fig:head_groups_regional_density}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{tails_density.png}
+        \caption{Tails}
+        \label{fig:tails_regional_density}
+  \end{subfigure}
+  \caption{Alternate figure : In all cases, the component radial distribution functions exhibit a
+	  composition gradient transitioning from the hydrophilic to the hydrophobic
+	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
+	  displaced (a), and sandwiched (b) configurations both show the highest
+	  concentrations of ions and head groups away from the pore center. Systems with
+	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
+	  concentrations of ions and head groups near the pore center, implying a more
+	  uniform, disordered pore.}~\label{fig:overlaid_densities}
+  \end{figure}
+
+% BJC5: old section
+%%MRS: I think you will need to refer back to names of the questions (or at least shortened versions of the names): people skimming the paper will not remember what the numbers are.
+%  In order to address question (\ref{point:poredefinition}), we plotted the
+%  number densities of heavy atoms in the head group, carbon atoms in the tail
+%  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
+%  region, we used the carbon atoms making up the aromatic ring. For the tail
+%  region we used only carbon atoms of the monomer tails (See Supporting
+%  Information for diagram). We average the histograms over at least 50 ns of
+%  equilibrated trajectory.
+%  
+%  In all cases, the space in the pore region is filled with sodium ions and
+%  head groups. Systems in the ordered pore basin are less dense in
+%  the center of the pore. In both the sandwiched and parallel displaced
+%  configurations, we see the density of head groups and sodium ions fall to less
+%  than 50\% of its maximum at r = 0 (Fig.~\ref{fig:layered_density}). The
+%  situation is most pronounced in the sandwiched configuration where the maximum
+%  head group density occurs 0.44 nm from the pore center. The parallel displaced
+%  configuration reaches its maximum 0.35 nm from the pore center. In contrast,
+%  both disordered pore systems show very little difference in density from its
+%  maximum. This implies a more uniform distribution of head groups within the
+%  pore center. This is the same conclusion drawn from the plots of $g(x,y)$ 
+%  (Figure~\ref{fig:xy_correlation}). 
+%  % High vacancy is less likely to be stable in the real system
+%
+%  There is a partition between the hydrophobic and hydrophilic regions, however
+%  it is a gradient in composition, rather than an abrupt division. The system
+%  does not confine sodium ions and head groups to just within the pore region.
+%  Assuming a pore radius of 0.6 nm, we see in all cases, that 19\% of sodium ions
+%  exist outside the pore region (except sandwiched, ordered pore, where 16\%
+%  are outside the pore). Additionally, we see that in all cases, about 3\% of the
+%  plotted tail density is located within the pore region (except sandwiched,
+%  ordered pore, where 1.5\% are within the pore region). These observations bring
+%  into question how one should define a pore in these types of systems. One
+%  usually measures a membrane's pore radius based on the size of a molecule it
+%  can reject, however it is not clear where the edges of the pores are and what
+%  size molecule would fit through. We leave these investigations for a future
+%  study.
+%
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.47\textwidth}
+%        \includegraphics[width=1\linewidth]{offset_density.png}
+%        \caption{Parallel Displaced, Ordered Pore Basin}
+%        \label{fig:offset_density}
+%  \end{subfigure}
+%  \begin{subfigure}{0.47\textwidth}
+%        \includegraphics[width=1\linewidth]{layered_density.png}
+%        \caption{Sandwiched, Ordered Pore Basin}
+%        \label{fig:layered_density}
+%  \end{subfigure}
+%  \begin{subfigure}{0.47\textwidth}
+%        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
+%        \caption{Parallel Displaced, Disorderd Pore Basin}
+%        \label{fig:disordered_offset_density}
+%  \end{subfigure}
+%  \begin{subfigure}{0.47\textwidth}
+%        \includegraphics[width=1\linewidth]{disordered_density.png}
+%        \caption{Sandwiched, Disordered Pore Basin}
+%        \label{fig:disorder_layered_density}
+%  \end{subfigure}
+%  \caption{In all cases, the component radial distribution functions exhibit a
+%	  composition gradient transitioning from the hydrophilic to the hydrophobic
+%	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
+%	  displaced (a), and sandwiched (b) configurations both show the highest
+%	  concentrations of ions and head groups away from the pore center. Systems with
+%	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
+%	  concentrations of ions and head groups near the pore center, implying a more
+%	  uniform, disordered pore.}~\label{fig:densities}
+%  \end{figure}
+
   \subsection{Effect of Water on Structure}
-
-  % BJC: I'm not sure this section is necessary anymore. The original point was to 
-  % see if we get more structure. It's not clear this is the right way to introduce
-  % water into the system. I think it confuses things.
-
-  %MRS6: good question.  It is interesting to see the swelling. We can talk.
 
@@
   	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
-  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm0 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
   	\includegraphics[width=.325\linewidth]{solvated_offset_rzplot_5.png}\\[-1ex]

### 2018-05-08 Ben_Manuscripts/structure_paper/supporting_information.tex
Edits, organization, renamings, figure additions

--- 2018-03-01 Ben_Manuscripts/structure_paper/supplemental.tex
@@
 
-\title{Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
+\title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
 \author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}
@@
 
-  \noindent
-  \begingroup
-	\fontsize{14pt}{14pt}\selectfont
-	\textbf{Further details regarding monomer parameterization} 
-  \endgroup
+%  \noindent
+%  \begingroup
+%	\fontsize{14pt}{14pt}\selectfont
+%	\textbf{Further details regarding monomer parameterization} 
+%  \endgroup
+  \section{Further details regarding monomer parameterization}\label{section:parameterization}
 
@@
 
-  \noindent
-  \begingroup
-        \fontsize{14pt}{14pt}\selectfont
-	\textbf{Calculation of pore-to-pore spacing statistics}
-  \endgroup
+  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.
 
-  \vspace{1em} 
-  We are interested in 5 pore-to-pore distances which should all be
-  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
-  the 5 distances are independent. We can calculate a trajectory of spacing
-  versus time for each of the 5 distances. We calculated the average pore-to-pore
-  spacing and its uncertainty according to the following procedure:
-   \begin{enumerate}
-	\item We calculated the time when each of the pore-to-pore distances
-	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
-	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
-	after the largest of the five values.
-	\item We calculated how long it takes for the data in each of the 5
-	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
-	\cite{chodera_simple_2016,shirts_statistically_2008}. 
-	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
-	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
-	five sub-trajectories of pore-to-pore spacings.   
-	\item We generate statistics using the bootstrapping technique. For
-	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
-	sampling from the trajectory blocks. 
-	\item The average pore-to-pore distance is the mean of all pore
-	spacings among all bootstrap trials.
-	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
-	pore spacing for each pore over all bootstrap trials. Using the 5 average 
-	pore-to-pore distances, we calculate the spread with:
-	\begin{align}
-	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
-	\end{align}
-	where $\overline{x}$ is the average pore-to-pore distance.
-  \end{enumerate}
-
-  \begin{figure}
-	\centering
-	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
-	\caption{There are five pore-to-pore distances that are equal in a perfect
-		hexagon. If each number in the diagram represents the center of a
-		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
-		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
-		are independent. For example, the distance from 1 to 4 is defined by
-		the location of all other pore centers.}
-	\label{fig:p2p_diagram}
-  \end{figure}
-
-  \vspace{1em}
-  \begingroup
-	\fontsize{14pt}{12pt}\selectfont
-	\noindent \textbf{Experimental correlation length of R-$\pi$}
-  \endgroup
-
-  \vspace{1em}
-  Experimentalists did not measure the correlation length, so we estimated it
-  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
-  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
-  intensity far from the pattern (high $q$) uniformly. We used a least squares
-  algorithm to fit a lorentzian curve to the data. Only values recorded above
-  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
-  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
-  maximum (FWHM) is related to the correlation length, L, by the relationship: $
-  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
-  of the diagonal entry of the covariance matrix of optimized fit paramaters. 
-  % need citations and more on lorentzian parameters
-  \begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.45\textwidth}	
-  	\includegraphics[width=\textwidth]{waxs_dashed.png}
-	\caption{}~\label{fig:waxs_dashed}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
-	\caption{}~\label{fig:correlation_length_exp}
-  \end{subfigure}
-  \caption{}~\label{fig:correlation}
-  \end{figure}
-  \vspace{1em} \\
-  %Our model is insensitive to initial configuration if monomer placement is chosen within reason. 
-  \begingroup
-	\fontsize{14pt}{12pt}\selectfont
-	\textbf{Initial Configuration Dependence}
-  \endgroup
+  \section{Initial Configuration Dependence}\label{section:initial_config_dependence}
+%  \begingroup
+%	\fontsize{14pt}{12pt}\selectfont
+%	\textbf{Initial Configuration Dependence}
+%  \endgroup
 
@@
 
-  \begin{enumerate}
+  %\begin{enumerate}
 
-	  \item \underline{Initial pore spacing}
+  %	  \item \underline{Initial pore spacing}
+  \subsection{Initial pore spacing}\label{section:initial_pore_spacing}
 
@@
 
-	  \item \underline{Initial pore radius}
+%	  \item \underline{Initial pore radius}
+	  \subsection{Initial pore radius}\label{section:initial_pore_radius}
 
@@
 
-	  \item \underline{Initial distance between layers}
+%	  \item \underline{Initial distance between layers}
+	  \subsection{Initial distance between layers}\label{section:initial_dbwl}
 
@@
 
+%  \end{enumerate}
+
+%  \noindent
+%  \begingroup
+%        \fontsize{14pt}{14pt}\selectfont
+%	\textbf{Calculation of pore-to-pore spacing statistics}
+%  \endgroup
+  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
+
+  \vspace{1em} 
+  We are interested in 5 pore-to-pore distances which should all be
+  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
+  the 5 distances are independent. We can calculate a trajectory of spacing
+  versus time for each of the 5 distances. We calculated the average pore-to-pore
+  spacing and its uncertainty according to the following procedure:
+   \begin{enumerate}
+	\item We calculated the time when each of the pore-to-pore distances
+	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
+	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
+	after the largest of the five values.
+	\item We calculated how long it takes for the data in each of the 5
+	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
+	\cite{chodera_simple_2016,shirts_statistically_2008}. 
+	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
+	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
+	five sub-trajectories of pore-to-pore spacings.   
+	\item We generate statistics using the bootstrapping technique. For
+	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
+	sampling from the trajectory blocks. 
+	\item The average pore-to-pore distance is the mean of all pore
+	spacings among all bootstrap trials.
+	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
+	pore spacing for each pore over all bootstrap trials. Using the 5 average 
+	pore-to-pore distances, we calculate the spread with:
+	\begin{align}
+	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
+	\end{align}
+	where $\overline{x}$ is the average pore-to-pore distance.
   \end{enumerate}
+
+  \begin{figure}
+	\centering
+	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
+	\caption{There are five pore-to-pore distances that are equal in a perfect
+		hexagon. If each number in the diagram represents the center of a
+		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
+		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
+		are independent. For example, the distance from 1 to 4 is defined by
+		the location of all other pore centers.}
+	\label{fig:p2p_diagram}
+  \end{figure}
+
+%  \vspace{1em}
+%  \begingroup
+%	\fontsize{14pt}{12pt}\selectfont
+%	\noindent \textbf{Experimental correlation length of R-$\pi$}\label{section:correlation_length}
+%  \endgroup
+
+  \subsubsection{\textit{The nematic order parameter}}\label{method:nematic_order}
+
+  We calculated the nematic order parameter for our system in order to
+  understand the degree of ordering among monomer head groups. Typically, the
+  nematic order parameter is calculated for nematic liquid crystal systems which
+  are characterized by unidirectional ordering of liquid crystal monomers. The
+  preferred direction of monomers is defined by the unit director vector,
+  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
+  order parameter, $S$, is defined as:
+  \begin{equation}
+	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
+	\label{eqn:nematic_order_parameter}
+  \end{equation}
+  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
+  In a perfectly ordered system, the molecular axis should be aligned with
+  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
+  quantifying the degree of monomer head group alignment between systems. We use
+  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
+  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
+  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
+  the aromatic head groups.
+
+  \section{Experimental correlation length of R-$\pi$}\label{section:correlation_length}
+
+  \vspace{1em}
+  Experimentalists did not measure the correlation length, so we estimated it
+  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
+  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
+  intensity far from the pattern (high $q$) uniformly. We used a least squares
+  algorithm to fit a lorentzian curve to the data. Only values recorded above
+  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
+  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
+  maximum (FWHM) is related to the correlation length, L, by the relationship: $
+  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
+  of the diagonal entry of the covariance matrix of optimized fit paramaters.
+  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
+  method. Since the experimental peak width is also influenced by strain and 
+  instrumental broadening in addition to finite size broadening, the value 
+  calculated here is really only an upper bound on the correlation length. 
+  % need citations and more on lorentzian parameters
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.45\textwidth}	
+  	\includegraphics[width=\textwidth]{waxs_dashed.png}
+	\caption{}~\label{fig:waxs_dashed}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
+	\caption{}~\label{fig:correlation_length_exp}
+  \end{subfigure}
+  \caption{}~\label{fig:correlation}
+  \end{figure}
+  \vspace{1em} \\
 
@@
 
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cc}
+  \toprule
+  System & Diffusion Constant ($m^2/s$) \\ 
+  \midrule
+  Sandwiched, Ordered & $1.4\mathrm{e}{-14}$ \\
+  Parallel Displaced, Ordered & $2.0\mathrm{e}{-14}$ \\
+  Sandwiched, Disordered & $2.0\mathrm{e}{-14}$ \\
+  Parallel Displaced, Disordered & $3.5\mathrm{e}{-14}$ \\
+  \bottomrule
+  \end{tabular}
+  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
+  which is three orders of magnitude lower than literature values.}~\label{table:msd}
+  \end{table}
+
   \begin{figure}

### 2018-05-08 HII/Scripts/correlation.py

@@ -116,19 +116,21 @@ def duplicate_periodically(pts, box):
     return p
 
 
-def sinusoidal_decay(x, a, b, c, d):
-    """
-    :param p: parameters: [period of oscillations, correlation time, amplitude, phase shift]
-    :param x: x axis values
-    :return: exponential function that sinusoidially decays to one
-    """
+def make_sinusoidal_decay(period):
+    def sinusoidal_decay(x, a, b, c):
+        """
+        :param p: parameters: [period of oscillations, correlation time, amplitude, phase shift]
+        :param x: x axis values
+        :return: exponential function that sinusoidially decays to one
+        """
 
-    return 1 + c*np.sin(a*x + d)*np.exp(-x/b)
+        return 1 - a*np.cos(period*x + b)*np.exp(-x/c)
+    return sinusoidal_decay
 
 
-def exponential_decay(x, L):
+def exponential_decay(x, a, L):
 
-    return 1 + np.exp(-x / L)
+    return 1 + a*np.exp(-x/L)
 
 
 def angle_average(X, Y, Z, SF, ucell=None):
@@ -195,6 +197,41 @@ def angle_average(X, Y, Z, SF, ucell=None):
     zfin = np.append(z[:, 0, :], z[1:, 0, :], axis=0)  # Z
 
     return final, rfin, zfin
+
+
+def autocorrelation(x, largest_prime=500):
+    """ FFT based autocorrelation function, which is faster than numpy.correlate. Efficiency is key in order to avoid
+    headaches.
+    :param x : multidimensional numpy array of y values of an equispaced timeseries. [npoints, ntrajectories]
+    :param largest_prime : the largest prime factor of array length allowed. The smaller the faster. 1.6M points takes
+    about 5 seconds with largest_prime=1000. Just be aware that you are losing data by truncating. But 5-6 data points
+    isn't a big deal usually.
+    """
+
+    # x -= np.mean(x, axis=0)  # subtract the mean (alternate, but not equivalent way of calculating autocorrelation)
+
+    # l = 2*x.shape[0] - 1
+    #
+    # while largest_prime_factor(l) >= largest_prime or l % 2 == 0:
+    #     l -= 1
+    #
+    # x = x[:(l + 1) // 2, :]
+
+    length = x.shape[0]*2 - 1
+
+    fftx = np.fft.fft(x, n=length)
+    ret = np.fft.ifft(fftx * np.conjugate(fftx))
+    ret = np.fft.fftshift(ret)
+
[…]

### 2018-05-08 HII/Scripts/gentop.py

@@ -94,6 +94,7 @@ class SystemTopology(object):
                     top.append(';Ion Topology\n')
                     top.append('#include "%s/ions.itp"\n' % self.top_location)
                     top.append('\n')
+                ion_count += 1
             else:
                 top.append(';%s Topology\n' % r)
                 if self.restraints:

### 2018-05-09 Ben_Manuscripts/structure_paper/Draft.tex
edits for the day

@@
 
-\makeatletter
-\newcommand*{\addFileDependency}[1]{% argument=file name and extension
-  \typeout{(#1)}
-  \@addtofilelist{#1}
-  \IfFileExists{#1}{}{\typeout{No file #1.}}
-}
-\makeatother
-
-\newcommand*{\myexternaldocument}[1]{%
-    \externaldocument{#1}%
-    \addFileDependency{#1.tex}%
-    \addFileDependency{#1.aux}%
-}
-
-\externaldocument[S-]{supplemental}
+\SectionNumbersOn
+
+%\makeatletter
+%\newcommand*{\addFileDependency}[1]{% argument=file name and extension
+%  \typeout{(#1)}
+%  \@addtofilelist{#1}
+%  \IfFileExists{#1}{}{\typeout{No file #1.}}
+%}
+%\makeatother
+% 
+%\newcommand*{\myexternaldocument}[1]{%
+%    \externaldocument{#1}%
+%    \addFileDependency{#1.tex}%
+%    \addFileDependency{#1.aux}%
+%}
+
+\externaldocument[S-]{supporting_information}
 
@@
   simulations of systems created with 4--8 columns per pore. We built systems in both
-  %BJC5: need to make parallel displaced and sandwiched configurations clear in methods
   the parallel displaced and sandwiched configurations and equilibrated them according
-  to the dry equilibration procedure. We test all systems with an initial vertical monomer 
-  spacing, \textit{d}, of 3.7~\AA in accordance with R-$\pi$. We tested 4 additional systems with
-  monomers initially spaced 5 \AA~apart vertically (See supporting info for more details on       
-  %BJC5: integrate supplemental section labels into main paper.
-  sensitivity to initial layer spacing). The pore-to-pore spacing is equilibrated, as defined in
-  section~\ref{method:equil_time} in all systems after 400 ns of simulation.
-  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested. 
+  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
+  spacing, \textit{d}, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
+  monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
+  of the supporting info for more details on sensitivity to initial layer spacing). 
+  The pore-to-pore spacing is equilibrated, as defined in section~\ref{method:equil_time},
+  % BJC5: this achemso format does not have section numbers so I can't reference sections
+  % within this document.
+  in all systems after 400 ns of simulation. Figure~\ref{fig:p2p} shows the equilibrated
+  pore-to-pore distances for all systems tested.
+
   Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
-  %BJC5: New paragraph? 
   consistent with the experimental value of 4.12 nm derived from SAXS measurements 
-  (Figure~\ref{fig:SAXS}).
-  %BJC5: comment about disordered systems
-
-  The remainder of this discussion will focus on the analysis of systems built with
-  5 columns per pore. Systems built with 6 columns per pore have an equilibrated
-  pore spacing c.a. 0.50 nm higher than experiment. Systems built with 4 columns per pore
-  %BJC5: edit above with consciencenous of new 6 mon/layer sim data
-  equilibrate to a pore spacing 0.25 nm lower than experiment. All systems tested are at least
-  metastable on the timescales studied here, however not all make physical sense or
-  fit the experimental profile that we are trying to match. In the limit of infinite simulation
-  time, all simulations will converge to a single density. It is our intention to choose an
-  initial configuration which quickly reaches a monomer density close to experiment. We believe
-  systems built with 5 columns per pore achieve this goal.
+  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
+  systems built with 5 columns per pore. Systems built with 6 columns per pore, and 
+  $\mathit{d}=3.7~\AA~$, have an equilibrated pore spacing c.a. 0.50 nm higher than experiment.
+  Systems built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower
+  than experiment.
+
+  %BJC5: thesis needs rewording.
+  Systems built with 6 columns-per-pore and $\mathit{d}=5~\AA~$ are not compact
+  in the z-direction. The final pore spacing is close to experiment within its uncertainty.
+  Relative to 6 column-per-pore systems started with $\textit{d}=3.7~\AA~$, the unit cell
+  is elongated in its z dimension and contracted in its x and y dimensions, however the
+  box volume stays nearly constant in all cases (Figure~\ref{fig:box_dimensions}). The system
+  is likely not fully equilibrated and may eventually rearrange into something that resembles
+  a 5 column-per-pore system. Further investigations into this are beyond the scope of this
+  paper.
+
+  \begin{figure}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{box_dimensions.png}
+  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5 \AA~$), the unit cell
+  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
+  constant across all cases. The y dimension box vectors are not included since we use 
+  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
+  \end{figure}
+
+  All systems tested are at least metastable on the timescales studied here, however not all 
+  make physical sense or fit the experimental profile that we are trying to match. In the limit
+  of infinite simulation time, all simulations will converge to a single density. It is our 
+  intention to choose an initial configuration which quickly reaches a monomer density close 
+  to experiment. We believe systems built with 5 columns per pore achieve this goal.
 
@@
 			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
-			 increases as the number of columns in each pore increases. The pore spacing
-			 of systems starting in the sandwiched configuration are systematically lower
-			 %BJC5: double check this statement once all data is present
-			 than those started in the parallel displaced configuration.}~\label{fig:p2p}
+			 increases as the number of columns in each pore increases.}~\label{fig:p2p}
   \end{figure}
@@
   R-pores appear in the expected location. R-pores is more intense than experiment, likely
-  because we are simulating a perfect, infinite hexagonal array. The real system has defects and
-  domain misalignment which decreases the overall intensity.
+  because we are simulating a near perfect, infinite hexagonal array. The real system has 
+  defects and domain misalignment which decreases the overall intensity.
   % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
@@
   R-spots appears to be weaker in the simulated patterns. They are also partially engulfed by
-  the wide R-$\pi$ reflection. We further explore R-spots in Section~\ref{section:rspots}.  
-  R-$\pi$ appears at a lower $q_z$ value than experiment. In all systems, the reflection 
-  reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack 
-  at least 4.2 \AA~apart rather than 3.7 \AA. This behavior is not surprising since GAFF models
-  atoms as point charges and does not appropriately model the aromatic $\pi-\pi$ interactions 
-  which would cause the monomers to stack closer together. We will explore R-$\pi$ in more detail
-  in Section~\ref{section:rpi}. R-double does not appear in any of the patterns. We will explore
-  its possible origins and reasons that it does not appear in our simulated patterns in
-  Section~\ref{section:rdouble}.
+  the wide R-$\pi$ reflection. R-$\pi$ appears at a lower $q_z$ value than experiment. In all
+  systems, the reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers 
+  prefer to stack at least 4.2 \AA~apart rather than 3.7 \AA. This behavior is not surprising 
+  since GAFF models atoms as point charges and does not appropriately model the aromatic
+  $\pi-\pi$ interactions which would cause the monomers to stack closer together. R-double 
+  does not appear in any of the patterns.
+
+%  We will explore its possible origins and reasons
+%  that it does not appear in our simulated patterns in Section~\ref{section:rdouble}.
 
@@
   alkanes, as seen in the experimental pattern.
-
-  %BJC4: This paragraph might fit better before qualitative description
-  %BJC5: This could potentially supplement parts of the qualitative descriptions.
+  %BJC5: not sure above sentence is clear (or necessary to say)
+
   We quantified the numerical discrepancies present when comparing the relative intensities
@@
   all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
-  equals 1.
-  % BJC5: above is stated in methods. Not sure if it needs to be restated.  
-  % BJC5: I need to explain how I calculated these intensities somewhere. Is this the right
-  % place to do it? I think it would just be confusing in the methods. I could also move it
-  % to supplemental.
-  % BJC5: Definitely need demonstrative figures in supporting info.
+  must equal 1.
+  % BJC5: show how intensities are measured in supporting info
   We measured the approximate intensity of R-$\pi$ by measuring the intensity of the peak shown
@@
   appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
-  cases. There is no R-double intensity to be measured.
+  cases. There is no R-double intensity to be measured. Descriptive figures are provided in the
+  supporting information to make these measurements clear.
 
@@
   \hline
-  Reflection & Experiment & Sandwiched & Parallel Displaced & Disordered Sandwiched & Disordered Parallel Displaced \\
+             &            &            & Parallel  & Disordered & Disordered         \\
+  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
   \midrule
@@
 %MRS5: put a little more of the rational for looking at this here. Why should they care?
+  We are most interested in the pore architecture. What's happening in the tails is unimportant.
+
   We plotted the number densities of heavy atoms in the head group, carbon atoms in the tail

### 2018-05-11 Ben_Manuscripts/structure_paper/Draft.tex
Edits and figure updates

@@
 \documentclass[journal=jpcbfk,manusciprt=article]{achemso}
+%\documentclass{article}
+%jpcbfk
 
@@
   	Ae^{-z/L}
+  	\label{eqn:decaying_exponential}
   \end{equation}
@@
   optimized fit parameters.
+
+  We also used $g(z)$ to calculate the equilibrated vertical stacking distance between
+  monomers, $\mathit{d}_equil$. 
+  %BJC5: in case there is an criticism of this method
+  %The simplest way to do so, would be to fourier transform
+  %$g(z)$ and extract the highest amplitude frequency of the resulting fourier series. 
+  %However, the size of our system limits the width of the bins in fourier space. The bins
+  %are too large to extract a precise value of $\mathit{d}_equil$. Instead, 
+  We fit a decaying sinusoidal function to $g(z)$ of the form:
+  \begin{equation}
+  	1 - Acos(\frac{2\pi}{\mathit{d}_{equil}}z + B)e^{-z/L}
+  	\label{eqn:decaying_sinusoid}
+  \end{equation}
+  where A and B are fit parameters for the function's amplitude and phase shift respectively.
+  This function could be used in place of Equation~\ref{eqn:decaying_exponential}, however
+  it does not fit the peaks of $g(z)$ from parallel displaced configurations well enough
+  to extract a reliable value of L.
+  %BJC5: maybe include plots of these fits in supporting info
 
@@
   to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
-  spacing, \textit{d}, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
+  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
   monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
   of the supporting info for more details on sensitivity to initial layer spacing). 
-  The pore-to-pore spacing is equilibrated, as defined in section~\ref{method:equil_time},
+  The pore-to-pore spacing was considered equilibrated, as defined in section~\ref{method:equil_time},
   % BJC5: this achemso format does not have section numbers so I can't reference sections
@@
 
+  All systems tested, although equilibrated from the perspective of the metrics used here, are
+  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
+  we are trying to match. In the limit of infinite simulation time, all systems will converge to
+  a single equilibrium configuration. For simplicity, we will group the systems studied here into
+  the ordered and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
+  ordered basin and any system where $\mathit{d}=5.0$ \AA will be included in the disordered basin.
+  The reason for these names will become clearer as we progress through our analysis.
+
+%    All systems tested are at least metastable on the timescales studied here, however not all 
+%  make physical sense or fit the experimental profile that we are trying to match. In the limit
+%  of infinite simulation time, all simulations will converge to a single density. It is our 
+%  intention to choose an initial configuration which quickly reaches a monomer density close 
+%  to experiment. We believe systems built with 5 columns per pore achieve this goal.
+
   Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
@@
   (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
-  systems built with 5 columns per pore. Systems built with 6 columns per pore, and 
-  $\mathit{d}=3.7~\AA~$, have an equilibrated pore spacing c.a. 0.50 nm higher than experiment.
-  Systems built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower
-  than experiment.
+  systems built with 5 columns per pore. Ordered basin systems built with 6 columns per pore,
+  have an equilibrated pore spacing c.a. 0.50 nm higher than experiment. Ordered basin systems
+  built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower than experiment.
 
   %BJC5: thesis needs rewording.
-  Systems built with 6 columns-per-pore and $\mathit{d}=5~\AA~$ are not compact
-  in the z-direction. The final pore spacing is close to experiment within its uncertainty.
-  Relative to 6 column-per-pore systems started with $\textit{d}=3.7~\AA~$, the unit cell
-  is elongated in its z dimension and contracted in its x and y dimensions, however the
-  box volume stays nearly constant in all cases (Figure~\ref{fig:box_dimensions}). The system
-  is likely not fully equilibrated and may eventually rearrange into something that resembles
-  a 5 column-per-pore system. Further investigations into this are beyond the scope of this
-  paper.
+  Disordered basin systems built with 6 columns-per-pore are not compact in the z-direction.
+  The final pore spacing is close to experiment within its uncertainty. Relative to ordered basin 
+  6 column-per-pore systems, the unit cell is elongated in its z dimension and contracted in its
+  x and y dimensions, however the box volume stays nearly constant in all cases 
+  (Figure~\ref{fig:box_dimensions}). The system is likely not fully equilibrated and may eventually
+  rearrange into something that resembles a 5 column-per-pore system. Further investigations 
+  into this are beyond the scope of this paper.
 
@@
 
-  All systems tested are at least metastable on the timescales studied here, however not all 
-  make physical sense or fit the experimental profile that we are trying to match. In the limit
-  of infinite simulation time, all simulations will converge to a single density. It is our 
-  intention to choose an initial configuration which quickly reaches a monomer density close 
-  to experiment. We believe systems built with 5 columns per pore achieve this goal.
-
   \begin{figure}
@@
   to experiment. We tested systems built with 5 columns per pore in the parallel 
-  displaced and sandwiched configurations at 300 K with monomers initially stacked
-  3.7 \AA~and 5.0 \AA~apart. We generated simulated patterns using portions
-  of simulation trajectory after equilibration. The patterns for all structures are
-  shown and compared to experiment in Figure~\ref{fig:XRDsim}.
+  displaced and sandwiched configurations at 300 K in the ordered and disordered
+  basins. We generated simulated patterns using portions of simulation trajectory after
+  equilibration. The patterns for all structures are shown and compared to experiment
+  in Figure~\ref{fig:XRDsim}.
 
@@
 	\caption{Simulated X-ray diffraction patterns show some qualitative agreement with 
-	experiment. Shown is a comparison of the (a) Sandwiched, d=3.7~\AA~ (b) Sandwiched,
-	d=5~\AA~(d) Parallel Displaced, d=3.7~\AA~ and (e) Parallel Displaced, d=5~\AA~ 
+	experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
+	disordered basin (d) Parallel Displaced, ordered basin and (e) Parallel Displaced, disordered basin 
 	configurations with (c) experimental WAXS. Quantitative comparisons of the relative 
@@
   systems, the reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers 
-  prefer to stack at least 4.2 \AA~apart rather than 3.7 \AA. This behavior is not surprising 
-  since GAFF models atoms as point charges and does not appropriately model the aromatic
-  $\pi-\pi$ interactions which would cause the monomers to stack closer together. R-double 
-  does not appear in any of the patterns.
+  prefer to stack at least 4.2 \AA~apart rather than 3.7 \AA. R-double does not appear in any
+  of the patterns.
 
@@
 
-  The simulated XRD pattern of the parallel displaced configuration shows an additional
-  reflection due to its helical structure. There are horizontal reflections near $|q_z|= 
+  The simulated XRD patterns of the parallel displaced configurations show an additional
+  reflection due to their helical structure. There are horizontal reflections near $|q_z|= 
   0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
@@
   \centering
-  \begin{tabular}{cccccc}
+  \begin{tabular}{c|ccccc}
   \toprule
@@
   \end{table}
+
+  %BJC5: I think something like this has to go somewhere.
+  The diffraction patterns show some noise, especially along the $q_z$ axis where $q_r$=0. This
+  noise can be suppressed by sampling more uncorrelated equilibrium configurations. Unfortunately,
+  our simulations are not long enough to sample enough independent configurations. Increasing the
+  number of trajectory frames used to simulate the structure factor within a given interval of time
+  does not offer any improvement.
+  %BJC5: maybe show in supplemental?
 
@@
   We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
-  is most intense in the sandwiched configuration (Figure~\ref{fig:sandwiched280K}). The relative 
-  intensity of R-spots is higher than in experiment (1.5 vs. 1.3). R-double is still not present.  
-  We will use this configuration to more thoroughly explore the origin of R-spots.
+  is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
+  The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3). R-double is still
+  not present. We will use this configuration to more thoroughly explore the origin of R-spots.
 
@@
   has attributed the spots in this particular WAXS pattern as the product of tilted alkane
-  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched
-  configuration simulated at 280K. We measured the tilt angle of the alkane chains and 
-  showed that our system equilibrates to an average tilt angle close to zero degrees
-  (Fig.~\ref{fig:tilt}).
-
-   %BJC5: bootstrap this data to make it smoother.
+  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched configuration simulated
+  at 280K. We measured the tilt angle of the alkane chains and showed that our system 
+  equilibrates to an average tilt angle of -2\degree (Fig.~\ref{fig:tilt}).
+
   \begin{figure}
@@
   The peaks in the nearest neighbor angle distribution are consistent with the
-  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
-  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
-  location where the highest intensity of spots are located on the simulated
-  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
-  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
-  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
+  location of R-spots. The peaks of interest in Figure \ref{fig:layered_tails}
+  are located at $\pm 33 \degree$ which is the same location where the highest
+  intensity of spots are located on the simulated patterns. We confirmed this 
+  conclusion by radially integrating the 2D WAXS pattern for 
+  $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
+  and 4.5 \AA~in real space). We observe distinct peaks ca. $30
   \degree$, in close agreement with the previously measured angle distribution
-  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
-  performed the same integration on the raw experimental data and found the angle
-  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
-  is a reconcilable difference with our simulated results.
+  (Figure~\ref{fig:layered_integration}). We performed the same integration on
+  the raw experimental data and found the angle at which R-spots reaches its
+  highest intensity to be $\pm 37 \degree$ which is a reconcilable difference
+  with our simulated results.
 
@@
   \begin{enumerate}
-  		\item The difference between 280K and 300K is small. Our forcefield parameters
-  		may not correctly model the behavior of the tails at 300K (citation?).
+  		\item The difference between 280 K and 300 K is relatively small. Our forcefield parameters
+  		may not correctly model the behavior of the tails at 300 K (citation?).
   		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
-  		If the head groups packed 3.7 \AA apart, the tails would be more confined and forced
+  		If the head groups packed 3.7 \AA~apart, the tails would be more confined and forced
   		to pack between vertically adjacent monomer tails. In our case, the tail region is
@@
   We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
-  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}).
-
-  %BJC5: redo after discussing with Michael
+  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). We used this 
+  information to understand how far apart monomers stack within monomer columns and
+  the degree to which they are correlated.
+
   \begin{figure}
@@
   \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
-  \caption{}\label{fig:z_correlation_sandwich}
+  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
   \end{subfigure}  
@@
   \includegraphics[width=\textwidth]{z_correlation_offset.png}
-  \caption{}\label{fig:z_correlation_offset}
+  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
   \end{subfigure}  
@@
   \centering
-  %BJC4: This is noisier than l=3.7 angstrom, but I can still pick out peaks. I'm unsure
-  % how to quantify the difference. The correlation length is very similar to the more
-  % ordered configuration.
   \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
-  \caption{}\label{fig:z_correlation_sandwich_disordered}
+  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
   \end{subfigure}  
@@
   \centering
-  %BJC4: There really aren't any good peaks here. 
   \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
-  \caption{}\label{fig:z_correlation_offset_disordered}
-  \end{subfigure}  
-  \caption{}\label{fig:correlation}
+  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
+  \end{subfigure}  
+  \caption{1D correlation functions of the center of masses of aromatic head groups, $g(z)$, show
+  decaying oscillatory behavior. We calculated the correlation length by fitting a decaying exponential
+  function (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The correlation length is
+  longer for ordered basin systems (Table~\ref{table:correlation_length}).
+  We did not attempt to calculate the correlation length for (d) because there are no clear peaks. We 
+  assume that its correlation is less than the vertical distance between monomers.}\label{fig:correlation}
   \end{figure}
 
-  %BJC5: conclusions here will need modification
-  The correlation length between stacked monomer head groups shows the best agreement with
-  experimental for systems simulated in the ordered basin.
-  %BJC4: explanation of correlation function calculation in methods section. 
-  %MRS5: the correlation length doesn't look like that great a fit, since it misses the first point by so much.  We may need to reevaluate a litle how this is done. 
-  %BJC5: forgot an amplitude on exponential fit. New results show lower correlation length
-  We calculated correlation length by fitting a decaying exponential function to all peaks of
-  $g(z)$ for the sandwiched configuration and to every other peak of $g(z)$ for the parallel
-  displaced configuration. The correlation length of systems simulated in the ordered basin are
-  11.2 \AA and 14.9 \AA	for the parallel displaced and sandwiched configurations respectively. 
-  %BJC5: Something about disordered systems.
-  Systems simulated in the ordered basin show correlation closest to the experimental correlation
-  length of 10.1 \AA. They are still slightly more correlated than experiment which would lead to
-  an increase in constructive X-ray scattering. 
-  %BJC5: this statement might not be true anymore.
-
-  Additionally, our system models near-perfectly straight pores with no defects which will
-  lead to higher intensity vertical stacking reflections. Nearly all of the intensity in R-$\pi$
-  of our simulated patterns is concentrated at a single point. Figure ~\ref{fig:intense_rpi}
-  shows the same simulated patterns with the upper boundary on the colorbar adjusted to be 6x
-  higher. The only distinguishable reflections are those of R-$\pi$ and R-pores. In the 
-  experimental pattern, the intensity is more evenly spread out over all of R-$\pi$.
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cccc}
+  \toprule
+  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
+  \midrule
+  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.5 $\pm$ 0.4            \\
+  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 15.5 $\pm$ 1.9           \\ 
+  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
+  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $\mathit{d}_{equil}$ \\ 
+  Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
+  \bottomrule
+  \end{tabular}
+  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
+  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
+  \label{table:correlation_length}
+  \end{table}
+
+  Monomers in the ordered basin stack closer together than those in the disordered basin
+  (Table~\ref{table:correlation_length}). We calculated the equilibrated vertical distance,
+  $\mathit{d}_{equil}$, between monomers using Equation~\ref{eqn:decaying_sinusoid}. 
+  Monomers in the ordered basin stack ca. 0.2 and 0.3 \AA~closer than those built in the 
+  disordered basin in the sandwiched and parallel displaced configurations respectively. 
+  The distance between stacked monomers is greater than experiment by 0.5 - 0.9 \AA~across all 
+  cases. This behavior is not surprising since GAFF models atoms as point charges and does not 
+  appropriately model the aromatic $\pi-\pi$ interactions which would cause the monomers to 
+  stack closer together. Ordered basin systems are likely the best choice for transport studies.
+
+  The correlation length between stacked monomer head groups of the ordered systems also show
+  closer agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
+  correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
+  not extract a reliable correlation length from the disordered parallel displaced configuration.
+  The amount of noise in the correlation function and the lack of an initial peak suggests that 
+  the correlation length is less than $\mathit{d}_{equil}$. In general, we see that correlation
+  length increases as monomers stack closer together. The same trend has been seen in molecular
+  dynamics studies of polymer fluids~\cite{koshy_density_2003}. We hypothesize that the correlation
+  length of the sandwiched configuration would increase to a value near experiment if monomers
+  packed closer together.
+
+  The persistent oscillatory behavior of the correlation function may in part explain the high
+  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
+  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
+  simulated systems, especially the sandwiched configurations, shows peaks which persist across
+  the entire correlation function. If the peaks at large values of z instead decay to 1 uniformly,
+  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
+  The monomer head groups in our simulations do not move enough to create the noise which would 
+  cause such behavior. See Section TBD of the supporting information for illustrative examples. 
+  % BJC5: Trying using inverted fourier transform of 2D experimental waxs. See what z-cross-section
+  % looks like (does it oscillate more or less?) Then take FT of that and compare its intensity
+  % to simulated intensity
+
+  The simulated intensity of R-$\pi$ is also more intense than experiment because our system
+  models near-perfectly straight pores with no defects. Nearly all of the intensity in 
+  R-$\pi$ of our simulated patterns is concentrated at a single point. Figure~\ref{fig:simulated_adjusted_colorbar}
+  shows the simulated pattern of the ordered sandwiched configuration with the upper boundary
+  on the colorbar adjusted to be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only
+  distinguishable reflections are those of R-$\pi$ and R-pores. In the experimental pattern 
+  (Figure~\ref{fig:experimental_adjusted_colorbar}, the intensity is more evenly spread out
+  over all of R-$\pi$. 
+  % BJC5: I'm not sure how well supported the above paragraph is by the below figure. Need to figure 
+  % out what to do about it
+  % BJC5: Could it also be related to noise in xy direction?
+  % BJC5 : I think my original intent was to explain it as tortuosity. But it's not clear if the
+  % reflection is arced
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{sandwich_rzplot_highlimit_cbar.png}
-  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections. Here, the 
-  colorbar was scaled so that the max is 6x higher than all other plots.}\label{fig:intense_rpi}
-  % BJC5: could benefit from an adjusted colorbar experimental pattern.
+  \begin{subfigure}{0.4\textwidth}
+	  \includegraphics[width=\linewidth]{sandwich_rzplot_highlimit_cbar.png}
+	  \caption{}\label{fig:simulated_adjusted_colorbar}
+  \end{subfigure}
+  \begin{subfigure}{0.4\textwidth}
+	  \includegraphics[width=\linewidth]{WAXS_raw_adjusted_colorbar.png}
+	  \caption{}\label{fig:experimental_adjusted_colorbar}
+  \end{subfigure}
+  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections in 
+  simulated diffraction patterns (a). Here, the colorbar was scaled so that the max is 6x
+  higher than all other plots.}\label{fig:intense_rpi}
   \end{figure}
@@
 %  ordered pore basin. Layers in the ordered pore basin are strongly correlated
-%  with neighboring layers up to more than 10 layers away. This behavior deviates
+%  with neighboring layers up to more than 10 layers away. This behavior deviatbecomes smalleres
 %  from experimental evidence. The experimental correlation length (See
@@
   al. showed that bulky carbonyl-containing substituents of stacked arene molecules tended to
-  tilt 45$\degree$ in order to relieve steric strain, thus allowing $\pi$-stacking between 
+  tilt 45$\degree$ in order to relieve steric strain, thus allowing $\pi$-$\pi$ stacking between 
   molecules, and to hydrogen bond with neighboring molecules. Lorenzo and Gra\~{n}a found 3
@@
   We can also produce R-double if layers are not uniformly spaced. Rather, monomers might form 
-  pairs that stack less than 3.7~\AA~apart, and whose center of masses are spaced 7.4 \AA 
+  pairs that stack less than 3.7~\AA~apart, and whose center of masses are spaced 7.4 \AA~ 
   from the next pair of monomers (Figure ~\ref{fig:staggered_rzplot_norestraints}). To our 
@@
   explanation for the appearance of R-double. The long-term stability of a configuration
-  similar to this may be feasible if monomers stay stacked 3.7 \AA apart.
+  similar to this may be feasible if monomers stay stacked 3.7 \AA~apart.
 
@@
   the position restriants are released.}\label{fig:rdouble}
-%MRS5: the conclusion seems like it actually may be ``this doesn't work either''.  How do they line up? Do they go to either parallel displaced or sandwiched?
   \end{figure}
 
-% BJC5 : Matt wants  a section like this somewhere.
   \subsection{Slow dynamics}
 
-  We observe unusually slow dynamics in our system. Typical diffusion constants
-  for columnar liquid crystals have been reported to be on the order of
-  $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
+  We observe unusually slow dynamics in our system relative to other liquid crysal
+  systems. Typical diffusion constants for columnar liquid crystals have been reported
+  to be on the order of $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
   constants of monomers in each of the systems we studied (See Table~\ref{S-table:msd}
@@
 
-%MRS5: put a little more of the rational for looking at this here. Why should they care?
-  We are most interested in the pore architecture. What's happening in the tails is unimportant.
+  We are most interested in the composition of the pores since we would like to study
+  transport mechanisms within them. We have shown that the tails possess a certain degree of order
+  which is necessary in order to create the complex WAXS pattern shown experimentally, but
+  they will not be involved in a separation process. We aim to further understand the pore
+  architecture and observe the differences, if any, between the different equilibrated
+  configurations studied so far.
 
   We plotted the number densities of heavy atoms in the head group, carbon atoms in the tail
-  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
-  region, we used the carbon atoms making up the aromatic ring. For the tail
-  region we used only carbon atoms of the monomer tails (See Supporting
-  Information for diagram). We average the histograms over at least 50 ns of
-  equilibrated trajectory.
-
-  In general, the composition of the pores is similar between all systems. We believe we can
-  study transport in any of the systems presented here and still extract valuable information.
-  We will need to verify that this assumption is true.
-
-  %BJC5: redo the numbers in this section.
-  In all cases, the space in the pore region is filled with sodium ions and
-  head groups. Systems in the ordered pore basin are less dense in
-  the center of the pore. In both the sandwiched and parallel displaced
-  configurations, we see the density of head groups and sodium ions fall to less
-  than 50\% of its maximum at r = 0 (Fig.~\ref{fig:layered_density}). The
-  situation is most pronounced in the sandwiched configuration where the maximum
-  head group density occurs 0.44 nm from the pore center. The parallel displaced
-  configuration reaches its maximum 0.35 nm from the pore center. In contrast,
-  both disordered pore systems show very little difference in density from its
-  maximum. This implies a more uniform distribution of head groups within the
-  pore center. This is the same conclusion drawn from the plots of $g(x,y)$ 
-  (Figure~\ref{fig:xy_correlation}).
+  region and all sodium ions (Figure~\ref{fig:overlaid_densities}). For the head group
+  region, we used heavy atoms making up the aromatic rings and carboxylate groups. For the tail
+  region we used carbon atoms of the monomer tails (See Figure S\ref{S-fig:monomer_color_coded}
+  for a diagram). We averaged the histograms over at least 50 ns of equilibrated trajectory.
 
@@
   does not confine sodium ions and head groups to just within the pore region.
-  Assuming a pore radius of 0.6 nm, we see in all cases, that 19\% of sodium ions
-  exist outside the pore region (except sandwiched, ordered pore, where 16\%
+  Based on size-exclusion experiments, we define the pore radius to be 0.6 nm
+  %BJC5 : Add vertical line to plots for 'pore radius'? Might be too busy.
+  ~\cite{zhou_supported_2005}. We see in all cases, that 19\% of sodium ions
+  exist outside the pore region (except sandwiched, ordered basin, where 16\%
   are outside the pore). Additionally, we see that in all cases, about 3\% of the
-  plotted tail density is located within the pore region (except sandwiched,
-  ordered pore, where 1.5\% are within the pore region). These observations bring
-  into question how one should define a pore in these types of systems. One
-  usually measures a membrane's pore radius based on the size of a molecule it
-  can reject, however it is not clear where the edges of the pores are and what
-  size molecule would fit through. We leave these investigations for a future
-  study.
-
-% BJC5 : Move this figure to supporting
+  plotted tail density is located within the pore region (except ordered sandwiched,
+  where 1.5\% are within the pore region). These observations bring into question how
+  one should define a pore in these types of systems. One usually measures a 
+  membrane's pore radius based on the size of a molecule it can reject, however
+  it is not clear where the edges of the pores are and what size molecule would
+  fit through. We leave these investigations for a future study.
+
+  In all cases, the space in the pore region is filled with a mixture of 
+  sodium ions and head groups. The ordered parallel displaced configuration has
+  the highest density of sodium ions at the pore centers. Both the ordered and 
+  disordered parallel displaced configurations have higher concentrations
+  of head groups in the center. This observation highlights that the pore region
+  is dense, not hollow, and may impede transport of solvent and solutes. We 
+  observe how this changes when water is added to the system.
+
+  In general, the composition of each region, particulary the pore region, is 
+  similar between all systems. We believe we can study transport in any of the
+  systems presented here and extract similar transport mechanisms. We will need
+  to verify that this assumption is true.
+
+% BJC5 : I think this is making progress towards a better representation of these plots. I
+% outlined the tops of the bars on the histograms so the individual rdf don't get covered.
+% I think it helps. I also varied the thickness of the outlines so that the farthest back 
+% line is thickest. That way, when the outlines overlap, you can see the ones in front.
   \begin{figure}
   \centering
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{offset_density.png}
-        \caption{Parallel Displaced, Ordered Pore Basin}
-        \label{fig:offset_density}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{layered_density.png}
-        \caption{Sandwiched, Ordered Pore Basin}
-        \label{fig:layered_density}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
-        \caption{Parallel Displaced, Disorderd Pore Basin}
-        \label{fig:disordered_offset_density}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{disordered_density.png}
-        \caption{Sandwiched, Disordered Pore Basin}
-        \label{fig:disorder_layered_density}
-  \end{subfigure}
-  \caption{In all cases, the component radial distribution functions exhibit a
-	  composition gradient transitioning from the hydrophilic to the hydrophobic
-	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
-	  displaced (a), and sandwiched (b) configurations both show the highest
-	  concentrations of ions and head groups away from the pore center. Systems with
-	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
-	  concentrations of ions and head groups near the pore center, implying a more
-	  uniform, disordered pore.}~\label{fig:densities}
-  \end{figure}
-
-%BJC5 : play with color scheme to make this viable
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.32\textwidth}
+  \begin{subfigure}{0.5\textwidth}
         \includegraphics[width=1\linewidth]{sodium_density.png}
@@
   \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
+  \begin{subfigure}{0.5\textwidth}
         \includegraphics[width=1\linewidth]{head_group_density.png}
@@
   \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
+  \begin{subfigure}{0.5\textwidth}
         \includegraphics[width=1\linewidth]{tails_density.png}
@@
   \end{subfigure}
-  \caption{Alternate figure : In all cases, the component radial distribution functions exhibit a
+  \caption{In all cases, the component radial distribution functions exhibit a
 	  composition gradient transitioning from the hydrophilic to the hydrophobic
@@
 
-% BJC5: old section
-%%MRS: I think you will need to refer back to names of the questions (or at least shortened versions of the names): people skimming the paper will not remember what the numbers are.
-%  In order to address question (\ref{point:poredefinition}), we plotted the
-%  number densities of heavy atoms in the head group, carbon atoms in the tail
-%  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
-%  region, we used the carbon atoms making up the aromatic ring. For the tail
-%  region we used only carbon atoms of the monomer tails (See Supporting
-%  Information for diagram). We average the histograms over at least 50 ns of
-%  equilibrated trajectory.
-%  
-%  In all cases, the space in the pore region is filled with sodium ions and
-%  head groups. Systems in the ordered pore basin are less dense in
-%  the center of the pore. In both the sandwiched and parallel displaced
-%  configurations, we see the density of head groups and sodium ions fall to less
-%  than 50\% of its maximum at r = 0 (Fig.~\ref{fig:layered_density}). The
-%  situation is most pronounced in the sandwiched configuration where the maximum
-%  head group density occurs 0.44 nm from the pore center. The parallel displaced
-%  configuration reaches its maximum 0.35 nm from the pore center. In contrast,
-%  both disordered pore systems show very little difference in density from its
-%  maximum. This implies a more uniform distribution of head groups within the
-%  pore center. This is the same conclusion drawn from the plots of $g(x,y)$ 
-%  (Figure~\ref{fig:xy_correlation}). 
-%  % High vacancy is less likely to be stable in the real system
-%
-%  There is a partition between the hydrophobic and hydrophilic regions, however
-%  it is a gradient in composition, rather than an abrupt division. The system
-%  does not confine sodium ions and head groups to just within the pore region.
-%  Assuming a pore radius of 0.6 nm, we see in all cases, that 19\% of sodium ions
-%  exist outside the pore region (except sandwiched, ordered pore, where 16\%
-%  are outside the pore). Additionally, we see that in all cases, about 3\% of the
-%  plotted tail density is located within the pore region (except sandwiched,
-%  ordered pore, where 1.5\% are within the pore region). These observations bring
-%  into question how one should define a pore in these types of systems. One
-%  usually measures a membrane's pore radius based on the size of a molecule it
-%  can reject, however it is not clear where the edges of the pores are and what
-%  size molecule would fit through. We leave these investigations for a future
-%  study.
-%
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.47\textwidth}
-%        \includegraphics[width=1\linewidth]{offset_density.png}
-%        \caption{Parallel Displaced, Ordered Pore Basin}
-%        \label{fig:offset_density}
-%  \end{subfigure}
-%  \begin{subfigure}{0.47\textwidth}
-%        \includegraphics[width=1\linewidth]{layered_density.png}
-%        \caption{Sandwiched, Ordered Pore Basin}
-%        \label{fig:layered_density}
-%  \end{subfigure}
-%  \begin{subfigure}{0.47\textwidth}
-%        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
-%        \caption{Parallel Displaced, Disorderd Pore Basin}
-%        \label{fig:disordered_offset_density}
-%  \end{subfigure}
-%  \begin{subfigure}{0.47\textwidth}
-%        \includegraphics[width=1\linewidth]{disordered_density.png}
-%        \caption{Sandwiched, Disordered Pore Basin}
-%        \label{fig:disorder_layered_density}
-%  \end{subfigure}
-%  \caption{In all cases, the component radial distribution functions exhibit a
-%	  composition gradient transitioning from the hydrophilic to the hydrophobic
-%	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
-%	  displaced (a), and sandwiched (b) configurations both show the highest
-%	  concentrations of ions and head groups away from the pore center. Systems with
-%	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
-%	  concentrations of ions and head groups near the pore center, implying a more
-%	  uniform, disordered pore.}~\label{fig:densities}
-%  \end{figure}
-
-  \subsection{Effect of Water on Structure}
+  \subsection{Effect of Water on Structure}\label{section:water}
 
@@
   (\ref{point:water}), by preparing parallel displaced and sandwiched
-  configurations according to the wet equilibration procedure. There is no
-  experimental measurement of trace water concentration in the pores so we tested
-  a range of water concentrations from 1 to 5 percent. Our lower bound models a
-  system with on average 2 water molecules for each monomer layer.
-  % BJC: double check this^ calculation or omit
-  Figure~\ref{fig:solvation} shows the simulated diffraction patterns resulting
-  from each configuration.
-
+  configurations according to the wet equilibration procedure. We limit
+  the discussion to the ordered pore basin since it produces equilibrated 
+  configurations closest to experiment. There is no experimental measurement
+  of trace water concentration in these membranes so we tested
+  a range of water concentrations from 1 to 5 percent. Figure~\ref{fig:solvation}
+  shows the simulated diffraction patterns resulting from each configuration.
+
+  % BJC5: maybe move this to supplemental. I think rdf and g(x,y) should be 
+  % enough to comment on the effect of water
   % formatting taken from : https://tex.stackexchange.com/questions/239715/add-titles-for-rows-and-columns-in-a-subfloat
@@
   wt\% water, R-$\pi$ and R-spots become nearly indistinguishable from R-alkanes.
-
   In systems built with 5 wt\% water, the pore region becomes filled with
@@
   We see that the pores become a mixture of water molecules and sodium ions (Fig.
-  \ref{fig:water_density}).
+  \ref{fig:water_density}). We also see that water exists in the tail region which 
+  may decrease the tail ordering and explain the decrease in intensity of R-spots.
 
@@
 
-  % BJC: unsure where or if this paragraph fits
-  % BJC: Probably as the last paragraph of this section
   Water is not necessary to maintain an ordered pore structure. We do not

### 2018-05-11 Ben_Manuscripts/structure_paper/supporting_information.tex
Edits and figure updates

@@
         \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
-	\caption{The groups used for $g(z)$ calculations. Red atoms are in the
+	\caption{The groups used for radial distribution calculations. Red atoms are in the
 		tails group. Green atoms are in the head group region. The blue atom is sodium. 
@@
 
+% BJC5 : Move this figure to supporting
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{offset_density.png}
+        \caption{Parallel Displaced, Ordered Pore Basin}
+        \label{fig:offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{layered_density.png}
+        \caption{Sandwiched, Ordered Pore Basin}
+        \label{fig:layered_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
+        \caption{Parallel Displaced, Disorderd Pore Basin}
+        \label{fig:disordered_offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{disordered_density.png}
+        \caption{Sandwiched, Disordered Pore Basin}
+        \label{fig:disorder_layered_density}
+  \end{subfigure}
+  \caption{In all cases, the component radial distribution functions exhibit a
+	  composition gradient transitioning from the hydrophilic to the hydrophobic
+	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
+	  displaced (a), and sandwiched (b) configurations both show the highest
+	  concentrations of ions and head groups away from the pore center. Systems with
+	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
+	  concentrations of ions and head groups near the pore center, implying a more
+	  uniform, disordered pore.}~\label{fig:densities}
+  \end{figure}
+
   \begin{figure}

### 2018-05-14 Ben_Manuscripts/structure_paper/Draft.tex
More edits

@@
 
-  We used the equilibrated parallel displaced system in the ordered pore basin
-  to calculate ionic conductivity since its structure is the closest match to
-  experiment. The model gives reasonable estimates of ionic conductivity when
+  We used equilibrated systems in the ordered pore basin to calculate ionic 
+  conductivity since we believe its structure is the closest match to
+  experiment. Our models give reasonable estimates of ionic conductivity when
   compared to experiment. We compare calculated values of ionic conductivity
   obtained using the Nernst-Einstein relation and Collective Diffusion model in
+  % names of equations capitalized?
   Figure~\ref{fig:conductivity}. The two methods agree with each other within
@@
         \centering
-        \includegraphics[width=0.5\linewidth]{IC_offset.png}
-        \caption{The collective diffusion model and the nernst-einstein relation yield
-        agreeing values of ionic conductivity. Both methods give calculated
-        values of ionic conductivity an order of magnitude higher than the experimental
-        value.}
+        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
+        \caption{The Collective Diffusion model and the nernst-einstein relation yield
+        agreeing values of ionic conductivity for both systems simulated. Both methods
+        estimate the value of the ionic conductivity to be an order of magnitude higher 
+        than the experimental value.}
         \label{fig:conductivity}
@@
 
-  Evidence strongly supports that monomers stay partitioned into layers which
-  stack to create pores and that each layer contains 5 monomers. We see periodic
-  spacing of layers based on the z-direction correlation function, $g(z)$, of
-  atoms in the tails and separately of atoms in the head groups. Systems not
-  built with 5 monomers per layer result in assemblies whose pore-to-pore spacing
-  is inconsistent with experiment.
-
-  We have explored the affect of two different $\pi$-$\pi$ stacking modes on
-  the equilibrated membrane structure. Simulated diffraction patterns generated
-  from MD trajectories suggest that the parallel-displaced configuration produces
-  a structure with the closest match to experiment.
-
-  We have observed a number of metastable configurations. We witnessed
-  long-term stability of systems built with a varied number of monomers per layer
-  as well as in different $\pi$-$\pi$ stacking configurations. We also examined
-  how the structure changes based on the initial distance between layers and
-  showed how systems differ when built with layers spaced 5~\AA~versus
-  3.7~\AA~apart. The configuration that showed the greatest agreement with
-  experiment was built in the parallel-displaced configuration, with 5 monomers
-  per layer and an initial layer spacing of 3.7 \AA.
+  We observed a number of metastable configurations, stable for hundreds of 
+  nanoseconds, which do not fit the experimental profile we have tried to match. 
+  We explored two classes of metastable basins which are dependent on the initial
+  vertical stacking distance between monomers : the ordered and disordered pore basins.
+  We expect that these metastable configurations will eventually rearrange and converge
+  to a single equilibrium structure. We conducted extensive analysis in order to 
+  isolate structures which most closely resembles the true equilibrium structure.
+
+  The system's pore spacing is most consistent with experiment when systems
+  are built with 5 columns per pore. The distance between pores increases with the 
+  number of columns per pore. Pores pack closer together in the disordered pore 
+  basin. Systems built with 6 columns per pore in the disordered basin expand in 
+  the z-direction which suggest that it may rearrange to 5 columns per pore long term.
+
+  We have maximized our model's consistency with the experimental WAXS pattern. We show
+  that R-alkanes and R-pores appear where expected. We learned that R-spots is likely 
+  due to ordered alkane chain packing. R-$\pi$ appears at lower q values than experiment
+  because monomer stack too far apart. We found that our model cannot reproduce R-double, 
+  however we have come up with a three different mechanisms that lead to the reflection's
+  appearance. The most likely explanation is that monomers within each column rotate ca.
+  15\degree with respect to their vertically adjacent neighbors so that tails can pack 
+  together more tightly.
 
   We characterized the environment centered around the membrane pores and
-  learned that the pores are generally filled by monomer head groups and sodium
-  ions. Membranes prepared in the sandwiched configuration have lower density 
-  pores. We also observed that there is not a hard partition between hydrophlic
-  and hydrophilic regions, rather there is a gradient.  This finding has raised
-  questions about the nature of any size-exclusion separations.
+  learned that the pores are generally filled with monomer head groups and sodium
+  ions. All systems studied showed a similar distribution of sodium, head groups 
+  and tails, which means we can study solute transport in any of the systems here
+  and extract similar transport mechanisms. We also observed that there is not a 
+  hard partition between hydrophlic and hydrophilic regions, rather there is a 
+  gradient. This finding has raised questions about the nature of size-exclusion separations.
 
@@
   Systems whose pores were filled with varying amounts of water showed a decrease
-  in structuring relative to dry systems.
+  in structuring relative to dry systems. At higher water concentrations, the pores
+  begin to swell, which may be more conducive to transport.
 
@@
 You cite some slower statistics, and there might be differences between lyotrpic and thermotropic, if the hydrophilic/hydrophobic effect is stronger than the effects in thermotropic fluids.
-  We acknowledge that our simulated system exhibits glassy dynamics. The
-  measured diffusion constants of monomers are three orders of magnitude lower
-  than expected. It is possible that our equilibration procedure induces these
-  types of metastable phases. It is also possible that the observed dynamics are
-  characteristic of the real system. We took great care to overcome the potential
-  limitations of our equilibration procedure and have come up with a structure
-  that is in good agreement with experimental data.
+%  We acknowledge that our simulated system exhibits glassy dynamics. The
+%  measured diffusion constants of monomers are one to three orders of magnitude lower
+%  than expected. It is possible that our equilibration procedure induces these
+%  types of metastable phases. It is also possible that the observed dynamics are
+%  characteristic of the real system. We took great care to overcome the potential
+%  limitations of our equilibration procedure and have come up with a structure
+%  that is in good agreement with experimental data.
 

### 2018-05-22 Ben_Manuscripts/structure_paper/Draft.tex
Modifications for paper

@@
   \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system (See supporting information). 
+  indicators of progress towards an ordered system (See section S~\ref{S-section:self_assembly}). 
   %BJC5: section showing self-assembly set up to be added
@@
   place between terminal vinyl groups present on each of the three monomer tails.
+  The reaction mechanism is drawn out in Figure S-\ref{S-fig:xlink_mech}.
   FRPs require an initiator which bonds to the system, meaning new atoms are
@@
   to readjust. For those reasons we did not cross-link all systems tested, but only
-  the most promising structure. We show that cross-linking does not significantly
+  the most promising structures. We show that cross-linking does not significantly
   change any of our drawn conclusions in Section 3.6.
@@
   the ordered and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
-  ordered basin and any system where $\mathit{d}=5.0$ \AA will be included in the disordered basin.
+  ordered basin and any system where $\mathit{d}=5.0$ \AA~will be included in the disordered basin.
   The reason for these names will become clearer as we progress through our analysis.
@@
   displaced and sandwiched configurations at 300 K in the ordered and disordered
-  basins. We generated simulated patterns using portions of simulation trajectory after
-  equilibration. The patterns for all structures are shown and compared to experiment
-  in Figure~\ref{fig:XRDsim}.
+  basins. We extended each simulation by 100 ns in order to get more equilibrated 
+  data. We generated simulated patterns using the extended of simulation trajectories
+  The patterns for all structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
 
@@
   % effects.
-  R-spots appears to be weaker in the simulated patterns. They are also partially engulfed by
-  the wide R-$\pi$ reflection. R-$\pi$ appears at a lower $q_z$ value than experiment. In all
-  systems, the reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers 
-  prefer to stack at least 4.2 \AA~apart rather than 3.7 \AA. R-double does not appear in any
-  of the patterns.
+  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
+  simulated patterns. They are also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
+  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
+  maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
+  rather than 3.7 \AA. R-double does not appear in any of the patterns.
 
@@
   of each reflection of interest between experimental and simulated patterns. Table 
-  ~\ref{table:relative_inensities_300K} quantifies the relative intensity of each reflection for 
+  ~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
   all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
@@
   appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
-  cases. There is no R-double intensity to be measured. Descriptive figures are provided in the
-  supporting information to make these measurements clear.
+  cases. There is no R-double intensity to be measured. Figures are provided in 
+  section S\ref{S-section:xrd_intensities} to make these measurements clear.
 
@@
   R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
-  R-spots   & 1.3 &  1.2 &  1.2 & 1.2 & 1.2  \\
-  R-$\pi$   & 2.8 & 18.1 & 14.2 & 7.8 & 10.0 \\
+  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
+  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
   R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
@@
   %BJC5: I think something like this has to go somewhere.
-  The diffraction patterns show some noise, especially along the $q_z$ axis where $q_r$=0. This
-  noise can be suppressed by sampling more uncorrelated equilibrium configurations. Unfortunately,
-  our simulations are not long enough to sample enough independent configurations. Increasing the
-  number of trajectory frames used to simulate the structure factor within a given interval of time
-  does not offer any improvement.
-  %BJC5: maybe show in supplemental?
+  The diffraction patterns show some noise, especially along the axis where $q_r$=0. This
+  noise can be suppressed by sampling more uncorrelated equilibrium configurations (See 
+  section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
+  to sample enough independent configurations. Increasing the number of trajectory frames
+  used to simulate the structure factor within a given interval of time does not offer 
+  any improvement.
 
@@
   the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
-  the centroids of the tails and measured the angle between each centroid and its
-  nearest neighbors with respect to the plane of the membrane. We see distinct
-  peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).
+  the centroids of the tails (Figure S-\ref{S-fig:centroids}) and measured the angle
+  between each centroid and its nearest neighbors with respect to the plane of the 
+  membrane. We see distinct peaks in the distribution of these angles 
+  (Figure~\ref{fig:tail_packing}).
 
@@
   The monomer head groups in our simulations do not move enough to create the noise which would 
-  cause such behavior. See Section TBD of the supporting information for illustrative examples. 
-  % BJC5: Trying using inverted fourier transform of 2D experimental waxs. See what z-cross-section
-  % looks like (does it oscillate more or less?) Then take FT of that and compare its intensity
-  % to simulated intensity
+  cause such behavior. See Section S\ref{S-section:rpi_ft} of the supporting information for
+  illustrative examples.
+
+  The system size does not significantly alter the intensity of R-$\pi$. We equilibrated a 
+  sandwiched system with twice as many monomers per column so that the system size doubled in 
+  the z-direction. The correlation length increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA, 
+  and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the correlation functions
+  are nearly identical (See Figure~\ref{S-fig:z_correlation_overlay}).
 
@@
   to be on the order of $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
-  constants of monomers in each of the systems we studied (See Table~\ref{S-table:msd}
-  in Supporting Information) and learned that they are all on the order of $10^{-14}~m^2/s$.
+  constants of monomers in each of the systems we studied (See Table S-\ref{S-table:msd}) 
+  and learned that they are all on the order of $10^{-14}~m^2/s$.
   Our systems may be frozen in a glassy state. It is also possible that we are simply 
@@
   autocorrelation function of the dihedral angle formed around the bond between the 
-  head groups and the ether oxygens which attach the tails to the head group. 
-  %BJC5: add diagram of which oxygens I'm talking about to the supporting info.
-  We exclude the dihedral from the middle tail since it is fundamentally different
-  than the two symmetric outside tails.
+  head groups and the ether oxygens which attach the tails to the head group 
+  (See Figure S\ref{S-fig:dihedrals}). We exclude the dihedral from the middle tail 
+  since it is fundamentally different than the two symmetric outside tails. We 
+  limited these studies to the sandwiched configuration for simplicity.
 
@@
   an unfavorable configuration. We implemented distance restraints between the centers of 
-  mass of monomer head groups to preserve the hexagonal phase (see Supporting Information
-  %BJC5: supporting info section on this doesn't exist yet.
-  for further detail), then rose the temperature of the equilibrated 300 K system to 500 K.
-  We witnessed decorrelation of tails after $\approx$ 11 ns with a plateau at 0, 
-  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed the 
-  resultant configuration back down to 300 K to see if the increased rotational freedom 
-  might allow the system to relax into to a more tightly packed configuration.
-  %BJC5: more to come.
+  mass of monomer head groups to preserve the hexagonal phase, then rose the temperature 
+  of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
+  decorrelation of ether dihedrals after $\approx$ 11 ns with a plateau at 0, 
+  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
+  the resultant configuration back down to 300 K over 200 ns to see if the increased rotational
+  freedom might allow the system to relax into to a more tightly packed configuration.
+
+  Decorrelating the ether dihedrals at high temperature, followed by thermal annealing
+  does not improve packing in our model. In the ideal case, if all monomers stacked 
+  3.7 \AA~ apart, the z-dimension of our unit cell should be 7.4 nm. In the ordered basin, 
+  sandwiched system studied in this paper, the z-dimension of the unit cell equilibrated 
+  to 8.87 nm, which is roughly consistent with the stacking distance reported in 
+  Table~\ref{table:correlation_length}. After 200 ns of annealing from 500K to 300K, the 
+  z-dimension of the unit cell was 9.22 nm. We repeated the annealing procedure over the 
+  course of 400 ns and the final z-dimension of the unit cell was 9.20 nm. Much longer
+  annealing simulations may get the system to the correct density, but we do not have
+  the resources to further explore this approach. 
+  % 800K simulations are worse. Over 400 ns, the z box dimension goes to 9.8. I think this
+  % is because the initial box z-box dimension is ~10.9. In the 500K system, the initial
+  % z-box dimension is ~9.7
 
@@
 
-  We explored the affect of water on pore structure, addressing question
+  We explored the effect of water on pore structure, addressing question
   (\ref{point:water}), by preparing parallel displaced and sandwiched
@@
   We used equilibrated systems in the ordered pore basin to calculate ionic 
-  conductivity since we believe its structure is the closest match to
+  conductivity since we believe their structures are the closest match to
   experiment. Our models give reasonable estimates of ionic conductivity when
@@
 
-  The system's structure and physical characteristics did not change
-  significantly when we applied the cross-linking algorithm to the equilibrated
-  parallel-displaced configuration in the ordered pore basin. We simulated
-  the cross-linked system in the NPT ensemble for 100 ns. After the system is
-  cross-linked, the distance between pores shrinks by 0.4 \AA~and the distance
-  between layers increases by 0.04 \AA. All major features are still present in
-  the simulated XRD patterns, however at lower intensities
-  (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using the
-  Nernst-Einstein relation and found that it is lower in the cross-linked system
-  (Fig.~\ref{fig:IC_xlink}).
-  %BJC: The current XRD pattern is from a 100 ns simulation. I am running it out
-  % longer to get more statistics
+  We applied our crosslinking algorithm to equilibrated sandwiched and parallel
+  displaced configurations in the ordered pore basin. We allowed the crosslinking
+  algorithm to propagate until greater than 90 \% of vinyl groups were either involved
+  in a crosslinking reaction or were terminated. See section S\ref{S-section:xlink}
+  for further details on the crosslinking algorithm. We allowed the crosslinked
+  configurations to simulate for 100 ns further in the NPT ensemble.
+
+  % BJC5: Is it worth including the distance between layers and the correlation length?   
+  There are minor changes to the physical characteristics of these systems when 
+  they are crosslinked (See Figure ~\ref{fig:xlink}). The ionic conductivity of 
+  the sandwiched configuration decreases while that of the parallel displaced 
+  configuration stays the same. The pore spacing decreases in both systems by
+  0.07 nm. The vertical monomer stacking distance increases in the sandwiched
+  configuration and decreases in the parallel displaced configuration, however the 
+  values of crosslinked configurations fall within uncertainty of their un-crosslinked
+  counterparts. The correlation length decreases in both systems, but is most 
+  pronounced in the parallel displaced system.
 
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{rzplot_xlink.png}
-	\caption{}~\label{fig:rzplot_xlink}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{IC_xlink.png}
-	\caption{}~\label{fig:IC_xlink}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{dbwl_xlink.png}
-	\caption{}~\label{fig:dbwl_xlink}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{p2p_xlink.png}
-	\caption{}~\label{fig:p2p_xlink}
-  \end{subfigure}
-  \caption{Applying our simulated crosslinking mechanism to an equilibrium
-	  configuration causes slight changes to the system's physical and structural
-	  properties. (a) Reflections produced by the cross-linked configuration are
-	  faded relative to the uncross-linked system. (b) The ionic conductivity is
-	  smaller relative to the uncross-linked system, but still much larger than the
-	  experimental value. When the system is cross-linked, the distance between
-	  layers increases (c) and the pore spacing decreases (d)}~\label{fig:xlink}
+  \includegraphics[width=\textwidth]{xlink_charts.eps}
+  \caption{There are minor differences between the physical properties of a
+  crosslinked (xlink) system versus an uncrosslinked system. The sandwiched configuration (S)
+  exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)
+  configuration remains constant. The pore spacing of both systems decreases upon crosslinking.
+  The vertical distance between stacked monomers increases in the sandwiched configuration
+  and decreases in the parallel displaced configuration. The correlation length decreases
+  in both configurations.}\label{fig:xlink}
   \end{figure}
+
+%  The system's structure and physical characteristics did not change
+%  significantly when we applied the cross-linking algorithm to the equilibrated
+%  parallel-displaced configuration in the ordered pore basin. We simulated
+%  the cross-linked system in the NPT ensemble for 100 ns. After the system is
+%  cross-linked, the distance between pores shrinks by 0.4 \AA~and the distance
+%  between layers increases by 0.04 \AA. All major features are still present in
+%  the simulated XRD patterns, however at lower intensities
+%  (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using the
+%  Nernst-Einstein relation and found that it is lower in the cross-linked system
+%  (Fig.~\ref{fig:IC_xlink}).
+
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%	\centering
+%	\includegraphics[width=\textwidth]{rzplot_xlink.png}
+%	\caption{}~\label{fig:rzplot_xlink}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%	\centering
+%	\includegraphics[width=\textwidth]{IC_xlink.png}
+%	\caption{}~\label{fig:IC_xlink}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%	\centering
+%	\includegraphics[width=\textwidth]{dbwl_xlink.png}
+%	\caption{}~\label{fig:dbwl_xlink}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%	\centering
+%	\includegraphics[width=\textwidth]{p2p_xlink.png}
+%	\caption{}~\label{fig:p2p_xlink}
+%  \end{subfigure}
+%  \caption{Applying our simulated crosslinking mechanism to an equilibrium
+%	  configuration causes slight changes to the system's physical and structural
+%	  properties. (a) Reflections produced by the cross-linked configuration are
+%	  faded relative to the uncross-linked system. (b) The ionic conductivity is
+%	  smaller relative to the uncross-linked system, but still much larger than the
+%	  experimental value. When the system is cross-linked, the distance between
+%	  layers increases (c) and the pore spacing decreases (d)}~\label{fig:xlink}
+%  \end{figure}
 

### 2018-05-22 Ben_Manuscripts/structure_paper/supporting_information.tex
Modifications for paper

@@
-\documentclass{article}
+\documentclass[journal=jpcbfk,manusciprt=article]{achemso}
 \usepackage{graphicx}
@@
 \usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
+%\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
 \usepackage{siunitx}
@@
 \usepackage{float}
+\usepackage{listings}
+\usepackage{xr}
+
+\SectionNumbersOn
+
+\externaldocument[M-]{draft}
 
@@
 
-%  \noindent
-%  \begingroup
-%	\fontsize{14pt}{14pt}\selectfont
-%	\textbf{Further details regarding monomer parameterization} 
-%  \endgroup
+  \section{Attempted Self-assembly}\label{section:self_assembly}
+
+  We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
+  generated using Packmol (\cite{martinez_packmol:_2009}). The input file given to 
+  Packmol is shown below.
+  \lstset{language=bash}
+  \begin{lstlisting}
+  tolerance 2.0
+  output packed.pdb
+  filetype pdb
+  structure monomer.pdb
+  		number 400
+  		inside box 0. 0. 0. 84.3 84.3 84.3
+  end structure
+  \end{lstlisting}
+
+  We used the same number of monomers (400) that we used in all other simulations. 
+  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
+  box with a volume of 660 $nm^3$, 25 \% larger than those used to create ordered unit
+  cells we studied.
+
+  We use the nematic order paramter as defined in section~\ref{method:nematic_order} to 
+  observe any progress towards an system ordering.
+
+  %BJC: picture of isotropic box (before and after?)
+  %BJC: plot of nematic order parameter vs. time
+
   \section{Further details regarding monomer parameterization}\label{section:parameterization}
@@
 
-  \begin{figure}
+  \begin{figure}[!htb]
 	\centering
@@
 
-  \begin{figure}
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{monomer_dihedrals.png}
+  \caption{We measured the autocorrelation functions of the dihedrals highlighted in
+  black. We only included dihedrals associated with the outer tails in our calculation
+  since the position of the center tail leads to fundamentally different interactions and
+  dynamics.}\label{fig:dihedrals}
+  \end{figure}
+
+  \begin{figure}[!htb]
         \centering
@@
   \end{figure}
+
+  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
+
+ %BJC: is it really necessary to explain this if I release the code? I don't explain
+ %any of the other stats I calculate.
+  \vspace{1em} 
+  We are interested in 5 pore-to-pore distances which should all be
+  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
+  the 5 distances are independent. We can calculate a trajectory of spacing
+  versus time for each of the 5 distances. We calculated the average pore-to-pore
+  spacing and its uncertainty according to the following procedure:
+   \begin{enumerate}
+	\item We calculated the time when each of the pore-to-pore distances
+	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
+	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
+	after the largest of the five values.
+	\item We calculated how long it takes for the data in each of the 5
+	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
+	\cite{chodera_simple_2016,shirts_statistically_2008}. 
+	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
+	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
+	five sub-trajectories of pore-to-pore spacings.   
+	\item We generate statistics using the bootstrapping technique. For
+	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
+	sampling from the trajectory blocks. 
+	\item The average pore-to-pore distance is the mean of all pore
+	spacings among all bootstrap trials.
+	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
+	pore spacing for each pore over all bootstrap trials. Using the 5 average 
+	pore-to-pore distances, we calculate the spread with:
+	\begin{equation}
+	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
+	\label{equation:p2p_stats}
+	\end{equation}
+	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
+	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
+	spacings.
+
+  \end{enumerate}
 
@@
         value for all our simulations in the main text.
-f		%The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
+        %The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
 		%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
@@
 		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
-		a distance where monomers in each pore no longer intersect adjacent pores. Once
+		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
 		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
@@
 
-	  \begin{figure}
+	  \begin{figure}[!htb]
 		\centering
@@
 	  %BJC: Could put vertical lines to indicate where position restraint values are reduced
-  	  \begin{figure}[htp]
+  	  \begin{figure}[!htb]
 		\centering
@@
 		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
-		agrees with the 2.5 \AA~configuration within error.
+		agrees with the 2.5 \AA~configuration within uncertainty.
 
@@
 
-	  \begin{figure}
+	  \begin{figure}[!htb]
 	  \centering
@@
 	  stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
-	  will focus the discussion here on systems built with layers stacked 10 \AA~
-	  apart.
+	  also tested a system built with layers stacked 10 \AA~ apart.
 
@@
 %  \endgroup
-  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
 
-  \vspace{1em} 
-  We are interested in 5 pore-to-pore distances which should all be
-  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
-  the 5 distances are independent. We can calculate a trajectory of spacing
-  versus time for each of the 5 distances. We calculated the average pore-to-pore
-  spacing and its uncertainty according to the following procedure:
-   \begin{enumerate}
-	\item We calculated the time when each of the pore-to-pore distances
-	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
-	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
-	after the largest of the five values.
-	\item We calculated how long it takes for the data in each of the 5
-	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
-	\cite{chodera_simple_2016,shirts_statistically_2008}. 
-	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
-	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
-	five sub-trajectories of pore-to-pore spacings.   
-	\item We generate statistics using the bootstrapping technique. For
-	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
-	sampling from the trajectory blocks. 
-	\item The average pore-to-pore distance is the mean of all pore
-	spacings among all bootstrap trials.
-	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
-	pore spacing for each pore over all bootstrap trials. Using the 5 average 
-	pore-to-pore distances, we calculate the spread with:
-	\begin{align}
-	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
-	\end{align}
-	where $\overline{x}$ is the average pore-to-pore distance.
-  \end{enumerate}
-
-  \begin{figure}
+  \begin{figure}[!htb]
 	\centering
@@
 
-%  \vspace{1em}
-%  \begingroup
-%	\fontsize{14pt}{12pt}\selectfont
-%	\noindent \textbf{Experimental correlation length of R-$\pi$}\label{section:correlation_length}
-%  \endgroup
-
-  \subsubsection{\textit{The nematic order parameter}}\label{method:nematic_order}
+  \section{The nematic order parameter}\label{method:nematic_order}
 
@@
   where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
-  In a perfectly ordered system, the molecular axis should be aligned with
-  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
-  quantifying the degree of monomer head group alignment between systems. We use
-  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
-  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
+  In a perfectly ordered nematic liquid crystal system, the molecular axis of each
+  monomer should be aligned with $\mathbf{n}$ and give an order parameter of $S=1$. 
+  We are interested in quantifying the degree of monomer head group alignment 
+  between systems. We use Eq.~\ref{eqn:nematic_order_parameter} to accomplish this
+  by defining $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
   $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
-  the aromatic head groups.
+  the aromatic head groups ($\mathbf{v}$ in Figure~\ref{fig:director}).
+
+  %BJC: change n to v in picture.
+  \begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.75\linewidth]{nematic_director.png}
+	\caption{We calculate the nematic order parameter by measuring the angle
+	between $\mathbf{v}$ and the z-axis.}~\label{fig:director}
+  \end{figure}
+
+  The nematic order parameter is highest in sandwiched systems. 
+  Figure~\ref{fig:nematic_distribution} shows the distribution of angles between
+  the nematic director and the vector perpendicular to the monomer head groups. 
+  Systems in the ordered basin have higher nematic order parameters than their
+  disordered basin counterparts. Both sandwiched system have higher nematic order
+  parameters than both parallel displaced systems. This may occur because monomers
+  in the sandwiched configuration have their motion restricted by vertically adjacent
+  monomers, while those in the parallel displaced configuration have more room to 
+  rotate.
+
+  \begin{figure}[!htb]
+
+  \begin{subfigure}{\linewidth}
+        \centering
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{layered_nematic_order.png}
+                \caption{Sandwiched, Ordered}~\label{fig:sandwich_nematic}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{offset_nematic_order.png}
+                \caption{Parallel Displaced, Ordered}~\label{fig:offset_nematic}
+        \end{subfigure}
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{disorder_sandwich_nematic_order.png}
+                \caption{Sandwiched, Disordered}~\label{fig:disorder_sandwich_nematic}
+        \end{subfigure}%
+        \begin{subfigure}{0.45\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{disorder_offset_nematic_order.png}
+                \caption{Parallel Displaced, Disordered}~\label{fig:disorder_offset_nematic}
+        \end{subfigure}
+
+  \end{subfigure}
+  \caption{The distribution of angles between nematic director vector (See
+	  Figure~\ref{fig:director}) and the z-axis averaged over the equilibrated portion
+	  of each trajectory}~\label{fig:nematic_distribution}
+  \end{figure}
+
+  \section{Measurement of intensities of experimental and simulated XRD patterns}\label{section:xrd_intensities}
+
+  We developed standardized methods of measuring the intensity of reflections of interest
+  in the experimental and simulated X-ray diffraction patterns presented in this work. Here,
+  we graphically illustrate the methods used for measuring these intensities.
+
+  All diffraction patterns are normalized according to R-alkanes and the intensities
+  of all reflections are reported relative to the intensity of R-alkanes. The region
+  used to calculate the average intensity of R-alkanes is shown in 
+  Figure~\ref{fig:ralkanes}. The top region is excluded because, in the simulated
+  patterns, R-$\pi$ intersects with R-alkanes.
+
+  R-$\pi$ and R-double are reported as the maximum values of the peaks of the 
+  $q_z$ cross-section of the experimental pattern at $q_r=0$ (Figure~\ref{fig:rpi_rdouble}).
+  In the case of the experimental pattern, the peak heights are not symmetrical,
+  so we report the average of the two heights.
+
+  We measured R-spots by calculating the average intensity within a region 
+  selected by visual inspection. We report the average intensity within the regions 
+  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernable
+  spots, we report the average intensity at the intersection of R-alkanes with
+  the $q_z$ value of R-double since that is where we expect it to appear based on
+  experiment. Since R-double does not appear in our simulated patterns, we 
+  estimate where it should appear as half of the $q_z$ value of R-$\pi$.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{WAXS_raw.png}
+  \caption{Unaltered experimental WAXS pattern}\label{fig:unaltered}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{ralkanes.png}
+  \caption{R-alkanes}\label{fig:ralkanes}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{rpi_rdouble.png}
+  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{rspots.png}
+  \caption{R-spots}\label{fig:rspots}
+  \end{subfigure}
+  \caption{}\label{fig:xrd_intensities}
+  \end{figure}
+
+  \section{Noise in simulated diffraction patterns}\label{section:xrd_noise}
+
+  The magnitude of noise in the simulated diffraction patterns decrease as 
+  the number of independent configurations increases. We simulated the structure
+  factor of 100 randomly placed particles and varied the number of independent 
+  configurations (N). It is expected that the structure factor should resemble
+  a two-dimsional gaussian. We cannot sample enough independent configurations
+  of our system to completely eliminate noise.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{xrd_1frame.png}
+  \caption{N=1}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{xrd_10frame.png}
+  \caption{N=10}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{xrd_100frame.png}
+  \caption{N=100}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{xrd_10000frame.png}
+  \caption{N=10000}
+  \end{subfigure}
+  \caption{The magnitude of noise, especially along $q_r$=0, decreases
+  as the number of independent configurations (N) increases.}\label{fig:xrd_noise}
+  \end{figure}
 
@@
   % need citations and more on lorentzian parameters
-  \begin{figure}[h]
+  \begin{figure}[!htb]
   \centering
@@
   \end{subfigure}
-  \caption{}~\label{fig:correlation}
+  \caption{(a) We estimated the system's experimental correlation length using a 
+  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a lorentzian curve 
+  to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
+  The correlation length is 1/FWHM.}~\label{fig:correlation}
   \end{figure}
@@
 
-% BJC5 : Move this figure to supporting
-  \begin{figure}
+  \begin{figure}[!htb]
   \centering
@@
 
-  \begin{figure}
-	\centering
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_layered_4.png}
-                \caption{4 mon/layer, Sandwiched}\label{fig:zdf_layered_4}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_offset_4.png}
-                \caption{4 mon/layer, Parallel Displaced}\label{fig:zdf_layered_4}
-        \end{subfigure}
-	\begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_layered_6.png}
-                \caption{6 mon/layer, Sandwiched}\label{fig:zdf_layered_6}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_offset_6.png}
-                \caption{6 mon/layer, Parallel Displaced}\label{fig:zdf_layered_6}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_layered_7.png}
-                \caption{7 mon/layer, Sandwiched}\label{fig:zdf_layered_7}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_offset_7.png}
-                \caption{7 mon/layer, Parallel Displaced}\label{fig:zdf_layered_7}
-        \end{subfigure}
-	\begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_layered_8.png}
-                \caption{8 mon/layer, Sandwiched}\label{fig:zdf_layered_8}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{zdf_offset_8.png}
-                \caption{8 mon/layer, Parallel Displaced}\label{fig:zdf_layered_8}
-        \end{subfigure}
-	\caption{$g(z)$ for all other configurations built with layers stacked 3.7 \AA~apart}\label{fig:zdf}
-  \end{figure}
+% BJC: Unnecessary, supporting info already long
+%  \begin{figure}
+%	\centering
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_layered_4.png}
+%                \caption{4 mon/layer, Sandwiched}\label{fig:zdf_layered_4}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_offset_4.png}
+%                \caption{4 mon/layer, Parallel Displaced}\label{fig:zdf_layered_4}
+%        \end{subfigure}
+%	\begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_layered_6.png}
+%                \caption{6 mon/layer, Sandwiched}\label{fig:zdf_layered_6}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_offset_6.png}
+%                \caption{6 mon/layer, Parallel Displaced}\label{fig:zdf_layered_6}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_layered_7.png}
+%                \caption{7 mon/layer, Sandwiched}\label{fig:zdf_layered_7}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_offset_7.png}
+%                \caption{7 mon/layer, Parallel Displaced}\label{fig:zdf_layered_7}
+%        \end{subfigure}
+%	\begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_layered_8.png}
+%                \caption{8 mon/layer, Sandwiched}\label{fig:zdf_layered_8}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_offset_8.png}
+%                \caption{8 mon/layer, Parallel Displaced}\label{fig:zdf_layered_8}
+%        \end{subfigure}
+%	\caption{$g(z)$ for all other configurations built with layers stacked 3.7 \AA~apart}\label{fig:zdf}
+%  \end{figure}
 
-  \begin{figure}
-	\centering
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{rzplot_layered_4.png}
-                \caption{4 mon/layer, Sandwiched}\label{fig:rzplot_layered_4}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{rzplot_offset_4.png}
-                \caption{4 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_4}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{rzplot_layered_6.png}
-                \caption{6 mon/layer, Sandwiched}\label{fig:rzplot_layered_6}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{rzplot_offset_6.png}
-                \caption{6 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_6}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{rzplot_layered_7.png}
-                \caption{7 mon/layer, Sandwiched}\label{fig:rzplot_layered_7}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{rzplot_offset_7.png}
-                \caption{7 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_7}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{rzplot_layered_8.png}
-                \caption{8 mon/layer, Sandwiched}\label{fig:rzplot_layered_8}
-        \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{rzplot_offset_8.png}
-                \caption{8 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_8}
-        \end{subfigure}
-	\caption{Simulated XRD patterns for all other configurations built with
-		 layers stacked 3.7 \AA~apart}\label{fig:XRDsim}
-  \end{figure}
+%BJC: unnecessary. Supporting info already long..and more is coming
+%  \begin{figure}
+%	\centering
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_layered_4.png}
+%                \caption{4 mon/layer, Sandwiched}\label{fig:rzplot_layered_4}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_offset_4.png}
+%                \caption{4 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_4}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_layered_6.png}
+%                \caption{6 mon/layer, Sandwiched}\label{fig:rzplot_layered_6}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_offset_6.png}
+%                \caption{6 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_6}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_layered_7.png}
+%                \caption{7 mon/layer, Sandwiched}\label{fig:rzplot_layered_7}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_offset_7.png}
+%                \caption{7 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_7}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_layered_8.png}
+%                \caption{8 mon/layer, Sandwiched}\label{fig:rzplot_layered_8}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_offset_8.png}
+%                \caption{8 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_8}
+%        \end{subfigure}
+%	\caption{Simulated XRD patterns for all other configurations built with
+%		 layers stacked 3.7 \AA~apart}\label{fig:XRDsim}
+%  \end{figure}
 
@@
 
-  \begin{figure}
-	\centering
-	\includegraphics[width=0.75\linewidth]{nematic_director.png}
-	\caption{We define the nematic director vector, $\mathbf{n}$, as the vector
-	perpendicular to the plane of the aromatic head group.}~\label{fig:director}
-  \end{figure}
-
-  \begin{figure}[ht]
-
-  \begin{subfigure}{\linewidth}
-        \centering
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{layered_nematic_order.png}
-                \caption{Sandwiched, Ordered}~\label{fig:sandwich_nematic}
-        \end{subfigure}%
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{offset_nematic_order.png}
-                \caption{Parallel Displaced, Ordered}~\label{fig:offset_nematic}
-        \end{subfigure}
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{disorder_sandwich_nematic_order.png}
-                \caption{Sandwiched, Disordered}~\label{fig:disorder_sandwich_nematic}
-        \end{subfigure}%
-        \begin{subfigure}{0.45\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{disorder_offset_nematic_order.png}
-                \caption{Parallel Displaced, Disordered}~\label{fig:disorder_offset_nematic}
-        \end{subfigure}
-
-  \end{subfigure}
-  \caption{The distribution of angles between nematic director vector (See
-	  Figure~\ref{fig:director}) and the z-axis averaged over the equilibrated portion
-	  of each trajectory}~\label{fig:nematic_distribution}
-  \end{figure}
-
-  \begin{figure}[!ht]
+  \begin{figure}[!htb]
         \centering
@@
 
-  \begin{figure}
+  \begin{figure}[!htb]
   \centering
@@
 
-  \noindent
-  \begingroup
-        \fontsize{14pt}{14pt}\selectfont
-        \textbf{Crosslinking Mechanism}
-  \endgroup
+  \section{Demonstrative fourier transforms}\label{section:fourier}
 
-  \vspace{1em}
+  Here we use Fourier transforms to demonstrate some of the arguments made in 
+  the main text. Interpretation of real and simulated X-ray diffraction patterns
+  is non-trivial and requires careful thought. They are a function of the positions
+  of all atoms in space, and suffer from the phase problem. Namely, there are multiple
+  solutions that could explain a single diffraction pattern. Using simplified models, 
+  we can hypothesize about the effect of various configurations on the simulated patterns.
+
+  \subsection{Magnitude of R-$\pi$}\label{section:rpi_ft}
+
+  In all cases, the magnitude of R-$\pi$ in our system is larger than that in experiment.
+  Some of the discrepancy can be explained by defects and imperfect pore alignment. 
+  However, there are significant effects resulting from the ordered states that we simulate.
+
+  Persistent oscillations in the z-correlation function, $g(z)$, increase the intensity of R-$\pi$. 
+  In Figure~\ref{fig:z_correlation}, we fit a decaying sinusoidal function 
+  (equation~\ref{M-eqn:decaying_sinusoid} of the main text) to $g(z)$ calculated from the
+  sandwiched configuration in the ordered basin. While the sinusoidal decay fit decays to one
+  rather quickly, $g(z)$ continues to oscillate with nearly the same amplitude as its third peak. 
+  In Figure~\ref{fig:theoretical_correlation_functions}, we overlay the same decaying sinusoidal
+  fit with a function that continues to oscillate with the same amplitude as the third peak of
+  the fit to $g(z)$. In Figure~\ref{fig:power_spectrum_comparison}, we plot the power spectrum
+  generated from the discrete Fourier transform of the plots in Figure~\ref{fig:theoretical_correlation_functions}. 
+  The maximum intensity of the power spectrum increases by nearly 60 \% when the correlation 
+  function does not decay to one. This explains, in part, the large simulated value of the
+  intensity of R-$\pi$.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{z_correlation_layered_sinefit.png}
+  \caption{}\label{fig:z_correlation}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{theoretical_correlation_functions.png}
+  \caption{}\label{fig:theoretical_correlation_functions}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{power_spectrum_comparison.png}
+  \caption{}\label{fig:power_spectrum_comparison}
+  \end{subfigure}
+  \caption{(a) We fit a decaying sinusoidal function to the z-correlation function, $g(z)$, 
+  calculated from the ordered basin sandwiched system. The oscillations in $g(z)$ continue
+  to oscillate at nearly the same amplitude as its third peak. (b) We overlaid a plot of the
+  fit to $g(z)$ with a similar function that continues to oscillate with the same amplitude
+  as its third peak. (c) The power spectrum of each plot in (b) exhibits a 60 \% increase in
+  intensity of the peaks when the function does not decay to 1.}\label{fig:rpi_ft}
+  \end{figure}
+
+  \subsection{Simplified assemblies}\label{section:simplified_assemblies}
+
+  We explored the sandwiched and parallel displaced configurations as potential ways for
+  aromatic head groups to stack. We used copies of the same monomer to build each system.
+  We were unable to create any assemblies which exhibited R-double using this technique. 
+  We simulated diffraction patterns of simplified configurations to understand why. We 
+  placed points in array that resemble the sandwiched and parallel displaced configurations.
+  Points are space 3.7 $\AA$ apart so it is easy to relate them to LLC membrane system.
+  5 columns of points are placed 5 $\AA$ from a defined "pore center".
+
+  When points are stacked in either configuration, R-double cannot appear. In the case
+  of the sandwiched configuration, the fundamental frequency is set at 1.7 $\AA^{-1}$,
+  the same location as R-$\pi$. Subharmonics appear at integer multiples of this frequency.
+  The parallel displaced configuration exhibits reflections at half the $q_z$ value of
+  R-$\pi$, which is where we expect to see R-double. However, just like the LLC membrane
+  system, the reflections appear away from $q_r=0$ and are caused by the helical stacking
+  arrangement.
+
+  From these observations, it is clear that, in order to make R-double appear in our simulated
+  diffraction patterns, we must create systems with asymmetries along the z-axis which lead to
+  a fundamental frequency of $0.85 \AA^{-1}$. This requires a modulation in electron density 
+  every 7.4 $\AA$. This line of thought gave rise to the systems studied in 
+  section~\ref{M-section:rdouble} of the main text.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{simple_sandwich_realspace.png}
+  \caption{}\label{fig:simple_sandwich_realspace}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{simple_sandwich_rzplot.png}
+  \caption{}\label{fig:simple_sandwich_rzplot}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{simple_offset_realspace.png}
+  \caption{}\label{fig:simple_offset_realspace}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{simple_offset_rzplot.png}
+  \caption{}\label{fig:simple_offset_rzplot}
+  \end{subfigure}
+  \caption{}\label{fig:simple_FTs}
+  \end{figure}
+
+  \section{Crosslinking algorithm details}\label{section:xlink}
+
   Crosslinking of the the monomer Na-GA3C11 occurs by a UV initiated free
@@
 
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{z_correlation_overlay.png}
+  \caption{The correlation functions generated from ordered basin sandwiched configurations
+  with different z-dimensions. The correlation function is nearly the same when the z-dimension
+  of the system is doubled.}\label{fig:z_correlation_overlay}
+  \end{figure}
+
 \clearpage

### 2018-05-22 HII/Scripts/Diffusivity.py

@@ -156,10 +156,10 @@ class Diffusivity(object):
 
         elif atoms:
 
-            selection = [a.index for a in t.topology.atoms if a.name in args.atoms]
+            selection = [a.index for a in t.topology.atoms if a.name in atoms]
 
-            atoms_per_residue = len(args.atoms)
-            matoms = np.array([Atom_props.mass[x] for x in args.atoms])
+            atoms_per_residue = len(atoms)
+            matoms = np.array([Atom_props.mass[x] for x in atoms])
             self.mres = np.sum(matoms)
         else:
             print('Error: No valid group of atoms or residues selected')
@@ -292,3 +292,4 @@ if __name__ == "__main__":
     D.ensure_fit()  # make sure diffusivity is being measured from the linear region of the MSD curve
     D.bootstrap(args.nboot)
     D.plot(args.axis)
+    print('D = %1.2e +/- %1.2e m^2/s' % (D.Davg, np.abs(D.Davg - D.confidence_interval[0])))

### 2018-05-25 Ben_Manuscripts/structure_paper/Draft.tex
Revisions and new figures

@@
 
-  \begin{figure}
+  \begin{figure}[!htb]
         \centering
@@
   systems built with 5 columns per pore. Ordered basin systems built with 6 columns per pore,
-  have an equilibrated pore spacing c.a. 0.50 nm higher than experiment. Ordered basin systems
+  have an equilibrated pore spacing ca. 0.50 nm higher than experiment. Ordered basin systems
   built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower than experiment.
@@
 
-  \begin{figure}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{box_dimensions.png}
-  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5 \AA~$), the unit cell
-  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
-  constant across all cases. The y dimension box vectors are not included since we use 
-  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
-  \end{figure}
-
-  \begin{figure}
+  \begin{figure}[!htb]
 	\centering
@@
 
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=\textwidth]{box_dimensions.png}
+  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5~\AA~$), the unit cell
+  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
+  constant across all cases. The y dimension box vectors are not included since we use 
+  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
+  \end{figure}
+
   \subsection{Structural refinement with 2D WAXS data}
@@
   basins. We extended each simulation by 100 ns in order to get more equilibrated 
-  data. We generated simulated patterns using the extended of simulation trajectories
+  data. We generated simulated patterns using the extended simulation trajectories.
   The patterns for all structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
 
+  % BJC5: I think something like this has to go somewhere.
+  The diffraction patterns show some noise, especially along the axis where $q_r$=0. This
+  noise can be suppressed by sampling more uncorrelated equilibrium configurations (See 
+  section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
+  to sample enough independent configurations. Increasing the number of trajectory frames
+  used to simulate the structure factor within a given interval of time does not offer 
+  any improvement.
+
   %BJC5: put figure letters in upper left hand corner of each pattern.
-  \begin{figure}[htb]
+  \begin{figure}[!htb]
 	\centering
@@
   R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
-  simulated patterns. They are also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
+  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
   appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
@@
   0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
-  $q_r = 0~\AA^{-1}$ so it does not appear for the same reason as R-double. This type of pattern
-  is characteristic of a helix (reference something).
+  $q_r = 0~\AA^{-1}$ so it does not necessarily appear for the same reason as R-double. 
+  This type of pattern is characteristic of a helix (reference something).
   %BJC5: reference something like a dna diffraction paper
-  It is possible that these reflections contribute to the continuation of R-double into R-
-  alkanes, as seen in the experimental pattern.
-  %BJC5: not sure above sentence is clear (or necessary to say)
+  It is possible that these reflections contribute to the diffuse reflections that connect
+  R-spots and R-double in the experimental pattern.
 
   We quantified the numerical discrepancies present when comparing the relative intensities
-  of each reflection of interest between experimental and simulated patterns. Table 
-  ~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
+  of each reflection of interest between experimental and simulated patterns. 
+  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
   all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
-  must equal 1.
-  % BJC5: show how intensities are measured in supporting info
-  We measured the approximate intensity of R-$\pi$ by measuring the intensity of the peak shown
-  by the cross-section of the 2D pattern at $q_r=0$. The relative intensity of R-$\pi$ is 
-  significantly higher than experiment in our simulations. R-spots is measured as the average
-  intensity within the region bounded by a 'spot'. Spots are identified based on visual 
-  inspection. If the spots were not easily discernable, then the intensity was taken as that of
-  the intersection of R-alkanes at half the $q_z$ value of R-$\pi$, since that is where it 
-  appears experimentally. The intensity of R-spots is slightly lower than experiment in all 
-  cases. There is no R-double intensity to be measured. Figures are provided in 
-  section S\ref{S-section:xrd_intensities} to make these measurements clear.
+  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
+  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
+  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
+  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
+  identified spots based on visual inspection. If the spots were not easily discernible, then the 
+  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
+  R-$\pi$, since that is where it appears experimentally. The intensity of R-spots is slightly
+  lower than experiment in all cases. There is no R-double intensity to be measured. Figures
+  are provided in section S\ref{S-section:xrd_intensities} to make these measurements clear.
 
@@
   \end{table}
-
-  %BJC5: I think something like this has to go somewhere.
-  The diffraction patterns show some noise, especially along the axis where $q_r$=0. This
-  noise can be suppressed by sampling more uncorrelated equilibrium configurations (See 
-  section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
-  to sample enough independent configurations. Increasing the number of trajectory frames
-  used to simulate the structure factor within a given interval of time does not offer 
-  any improvement.
+  %BJC5: Bold font is caused by achemso document type
 
@@
 
-  \begin{figure}
+  \begin{figure}[!htb]
 	  \begin{subfigure}{0.45\linewidth}
@@
   the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
-  the centroids of the tails (Figure S-\ref{S-fig:centroids}) and measured the angle
+  the centroids of the tails (Figure S\ref{S-fig:centroids}) and measured the angle
   between each centroid and its nearest neighbors with respect to the plane of the 
@@
   intensity of spots are located on the simulated patterns. We confirmed this 
-  conclusion by radially integrating the 2D WAXS pattern for 
+  by radially integrating the 2D WAXS pattern for 
   $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
@@
   \midrule
-  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.5 $\pm$ 0.4            \\
-  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 15.5 $\pm$ 1.9           \\ 
+  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
+  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
   Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
@@
   correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
-  not extract a reliable correlation length from the disordered parallel displaced configuration.
-  The amount of noise in the correlation function and the lack of an initial peak suggests that 
-  the correlation length is less than $\mathit{d}_{equil}$. In general, we see that correlation
-  length increases as monomers stack closer together. The same trend has been seen in molecular
-  dynamics studies of polymer fluids~\cite{koshy_density_2003}. We hypothesize that the correlation
-  length of the sandwiched configuration would increase to a value near experiment if monomers
-  packed closer together.
+  not extract a reliable correlation length from the disordered parallel displaced configuration
+  since the peak heights do not decay significantly. 
+  %The amount of noise in the correlation function and the lack of an initial peak suggests that 
+  %the correlation length is less than $\mathit{d}_{equil}$.
+  In general, we see that correlation length increases as monomers stack closer together. The same
+  trend has been seen in molecular dynamics studies of polymer fluids~\cite{koshy_density_2003}.
+  We hypothesize that the correlation length of the sandwiched configuration would increase to a
+  value near experiment if monomers packed closer together.
 
@@
   simulated systems, especially the sandwiched configurations, shows peaks which persist across
-  the entire correlation function. If the peaks at large values of z instead decay to 1 uniformly,
+  the entire correlation function. If the peaks, at large values of z, instead decay to 1 uniformly,
   the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
@@
   distinguishable reflections are those of R-$\pi$ and R-pores. In the experimental pattern 
-  (Figure~\ref{fig:experimental_adjusted_colorbar}, the intensity is more evenly spread out
+  (Figure~\ref{fig:experimental_adjusted_colorbar}), the intensity is more evenly spread out
   over all of R-$\pi$. 
@@
   calculated the structure factor of simple systems that mimic the parallel
-  displaced and sandwiched configurations. Neither give rise to R-double. (See Figure "fourier
-  transforms of simple systems" in supporting info). The appearance of R-double implies a
+  displaced and sandwiched configurations. Neither give rise to R-double. 
+  (See section S~\ref{S-section:simplified_assemblies}). The appearance of R-double implies a
   vertical modulation in electron density every 7.4 \AA. It is possible that this modulation 
-  occurs in either the head or the tails. There is a not a unique solution to this problem,
-  however we can speculate based on what makes the most physical sense.
+  occurs in either the head or the tails. It is also possible that R-double does not appear in
+  a completely dry system. We will address this point in section~\ref{section:water}. There is
+  a not a unique solution to this problem, however we can speculate based on what makes the most
+  physical sense.
 
@@
   of carboxylate groups attached to phenyl rings since the group extends the system's 
-  $\pi$ conjugation. (citation) (See figure in supporting info with energy barrier plots)
+  $\pi$ conjugation (citation) (See Figure S\ref{S-fig:carboxylate_dihedral_rb}).
   %BJC5: add citation for extended pi conjugation
-  %BJC5: add figure reference and figure to supporting info
   There are instances where carboxylate groups in other systems rotate out of plane. Bushey et
@@
   fades after a few nanoseconds of simulation. Still, this may be the most reasonable
-  explanation for the appearance of R-double. The long-term stability of a configuration
+  way for R-double to appear in a dry system. The long-term stability of a configuration
   similar to this may be feasible if monomers stay stacked 3.7 \AA~apart.
 
-  \begin{figure}[htb]
+  \begin{figure}[!htb]
   \centering
@@
   \subsection{Slow dynamics}
+
+  %BJC5: this section may fit better after the next one?
 
@@
 
-  There is not enough movement on the timescales we simulated for the system to 
+  Consequently, there is not enough movement on the timescales we simulated for the system to 
   consistently reach a structure equivalent to experiment. In all cases our monomers
@@
   While this may be in large part due to the forcefield's inability to model aromatic
-  interactions, it is also possible that the monomer tails do not pack as tightly as 
-  they could. More densely packed tails could allow the monomers to stack closer 
-  together.
+  interactions, it is also possible that the monomer tails do have enough time to pack 
+  as tightly as they could. More densely packed tails could allow the monomers to stack
+  closer together.
 
@@
   of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
-  decorrelation of ether dihedrals after $\approx$ 11 ns with a plateau at 0, 
+  decorrelation of the ether dihedrals after $\approx$ 11 ns with a plateau at 0, 
   (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
@@
   In general, the composition of each region, particulary the pore region, is 
-  similar between all systems. We believe we can study transport in any of the
-  systems presented here and extract similar transport mechanisms. We will need
-  to verify that this assumption is true.
+  similar between all systems. We believe we can solvate and study transport in any
+  of the systems presented here and extract similar transport mechanisms. We will 
+  need to verify that this assumption is true.
 
@@
 % line is thickest. That way, when the outlines overlap, you can see the ones in front.
-  \begin{figure}
+  \begin{figure}[!htb]
   \centering
@@
 
-  \subsection{Effect of Water on Structure}\label{section:water}
+  \subsection{The Effect of Water on Structure}\label{section:water}
 
@@
   configurations according to the wet equilibration procedure. We limit
-  the discussion to the ordered pore basin since it produces equilibrated 
-  configurations closest to experiment. There is no experimental measurement
-  of trace water concentration in these membranes so we tested
-  a range of water concentrations from 1 to 5 percent. Figure~\ref{fig:solvation}
-  shows the simulated diffraction patterns resulting from each configuration.
-
-  % BJC5: maybe move this to supplemental. I think rdf and g(x,y) should be 
-  % enough to comment on the effect of water
+  the discussion to the ordered pore basin since it produces the most experimentally
+  consistent equilibrated configurations. There is no experimental measurement
+  of trace water concentration in these membranes so we tested a range of water
+  concentrations from 1 to 5 percent. Figure~\ref{fig:solvation} shows the simulated
+  diffraction patterns resulting from each configuration.
+
   % formatting taken from : https://tex.stackexchange.com/questions/239715/add-titles-for-rows-and-columns-in-a-subfloat
@@
 
-  \begin{figure}
+  \begin{figure}[!htb]
+  \begin{subfigure}{0.915\textwidth}
   	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
@@
   	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
-  	\includegraphics[width=.28\linewidth,trim={1cm0 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
-  	\includegraphics[width=.325\linewidth]{solvated_offset_rzplot_5.png}\\[-1ex]
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_5.png}\\[-1ex]
   	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
@@
   	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
-  	\includegraphics[width=.325\linewidth]{solvated_layered_rzplot_5.png}\\[-1ex]
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_5.png}\\[-1ex]
   	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
   	\end{tabular}
-	\caption{Simulated XRD patterns indicate that systems with added water
-		are not as structured as the dry systems. As increasing amounts of water are 
-		added to both systems, R-$\pi$ fades. When 2.5 wt\% water is added to the
-		sandwiched system, R-$\pi$ gains back some intensity, but its magnitude is not
-		greater than the dry system. R-spots also disappears as water is added. It is
-		absent in all parallel displaced simulations, but fades gradually as water is
-		added to the sandwiched configuration.}%
+  \end{subfigure}
+  \begin{subfigure}{0.075\textwidth}
+  	\includegraphics[width=\textwidth]{colorbar_jet.png}
+  \end{subfigure}
+	\caption{Adding 1 wt \% water to the ordered basin dry systems causes an increase in the intensity
+	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
+	of water only increase discrepancies with experiment.}%
   \label{fig:solvation}
@@
 
-  In all cases, water disrupts structuring of the model. When we add water to
-  the system, the intensity of the reflections decrease. In systems built with 5
-  wt\% water, R-$\pi$ and R-spots become nearly indistinguishable from R-alkanes.
-  In systems built with 5 wt\% water, the pore region becomes filled with
-  water. We plotted the number density of components in this system. As with the 
-  dry systems, we see a gradual compositional transition from hydrophilic to hydrophobic.  
-  We see that the pores become a mixture of water molecules and sodium ions (Fig.
-  \ref{fig:water_density}). We also see that water exists in the tail region which 
-  may decrease the tail ordering and explain the decrease in intensity of R-spots.
-
-  The membrane swells when we introduce water. The location of maximum head
-  group density shifts from 0.35 to 0.62 nm and from 0.44 to 0.61 nm in the
-  parallel displaced and sandwiched configurations respectively. Again, we
-  observe the existence of ions, head groups and water outside the pore region,
-  however in the hydrated system, the head groups drift beyond 1.5 nm from the
-  pore center. In the dry systems, head groups did not wander beyond 1.4 nm from
-  the pore center. Both observations suggest that water pushes all components
-  radially outward from the pore center, characteristic of a swelling process.
-  The plots of $g(x,y)$ for dry and wet systems are compared in
-  Figure~\ref{fig:solvated_correlation}. They further illustrate how the system
-  swells in the presence of water. This system is a closer representation
-  of the H\textsubscript{II} phase which is typically synthesized with ca. 8 wt\%
-  water. Further investigation of hydrated systems can help unravel the
-  mechanisms for selective transport in separations of aqueous solutions.
-
-  Water is not necessary to maintain an ordered pore structure. We do not
-  eliminate the possibility that water is necessary in order to drive
-  self-assembly, but studying the mechanisms of self-assembly is beyond the
-  scope of this work. According to our model, once the system has formed the
-  Col\textsubscript{h} phase, adding water only drives disorder of the pore
-  structure. In the true equilibrium configuration, if water exists, it is
-  primarily confined to the pore region where there is no driving force for
-  aggregation of water molecules. In the case of trace water, water molecules
-  will be too sparse to form a hydrogen bonding network.
-
-  \begin{figure}
+  The addition of water allows R-double to appear. When we add 1 wt\% water to the 
+  parallel displaced configuration, R-double becomes visible (Figure~\ref{fig:rdouble_offset}). 
+  When 2.5 wt\% water is added, R-double disappears, but the helical reflections characteristic
+  of the parallel displaced configuration become more diffuse, which is a closer match to 
+  experiment. If water is truly responsible for R-double, then the there is likely
+  between 1 and 2.5 wt\% water absorbed into the membrane. This does not exclude 
+  possible contributions from the motifs discussed in section~\ref{section:rdouble}. Water
+  may facilitate the stability of such motifs. 
+%  However, given the long-term stability of this configuration, it is most likely that small
+%  amounts of water are responsible for the existence of R-double.
+
+  The systems studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} were not truly
+  thermotropic Col\textsubscript{h} phases. Rather, they were very low water content 
+  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity.
+  This detail may be important for reproducing the results of Feng et al.
+
+  Water causes the monomer head groups to restructure. We confirmed that the reflection is 
+  not caused by the water itself. We removed all water molecules from the trajectory and 
+  showed that R-double is still present in the simulated diffraction pattern 
+  (Figure~\ref{fig:rdouble_nowater}). We also confirmed that the tails are not responsible for
+  R-double. R-double is not present when we remove all atoms except carbon atoms that make
+  up the tails (Figure~\ref{fig:rdouble_tails}). It is clear that interactions between water
+  and head groups causes them to restructure in a way that leads to R-double.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
+  \caption{Full system}\label{fig:rdouble_offset}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{rdouble_nowater_rzplot.png}
+  \caption{Water removed}\label{fig:rdouble_nowater}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{rdouble_tails_only_rzplot.png}
+  \caption{Tails only}\label{fig:rdouble_tails}
+  \end{subfigure}
+  \caption{The structure of the head groups is responsible for the appearance of
+  R-double in (a). Removing water from the trajectory (b) results in a simulated 
+  diffraction pattern nearly identical to that in (a). R-double is not present
+  when we simulate the diffraction pattern of system where only tails are present. 
+  (c)}\label{fig:rdouble_origin}
+  \end{figure}
+
+  The appearance of R-double may be due to increased order of the pores. The first
+  peak of the correlation function, $g(z)$, is approximately 30 \% larger in the 
+  solvated versus dry configuration (Figure~\ref{fig:solvated_correlation_overlay}).
+  Based on the peak locations, it is evident that the head groups stack closer 
+  together in the solvated configuration which may play a role in enforcing order.
+  This may be in part due to swelling of the pores. In 
+  Figure~\ref{fig:head_group_density_overlay} there is a clear decrease in 
+  head group density within 0.4 nm of the pore center. Water molecules may swell 
+  the pores and hydrogen bond with monomer head groups, tethering the monomers 
+  closer together. If this is the case, then it implies that R-double has always
+  been at least weakly present in the simulated diffraction patterns, but may 
+  have been buried by noise.
+
+  \begin{figure}[!htb]
   \centering
   \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=1\linewidth]{offset_solvated_density.png}
-        \caption{Parallel Displaced}
-        \label{fig:offset_solvated_density}
+  \includegraphics[width=\textwidth]{solvated_correlation_overlay.png}
+  \caption{}\label{fig:solvated_correlation_overlay}
   \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
-        \includegraphics[width=1\linewidth]{layered_solvated_density.png}
-        \caption{Sandwiched}
-        \label{fig:layered_solvated_density}
-  \end{subfigure}
-  \caption{Water fills the membrane pores in the parallel displaced (a) and
-	  sandwiched (b) configurations. Head groups in the sandwiched configuration sit
-	  closer to the pore center than they do in the parallel displaced configuration.
-	  Both systems are composed primarily of water close to the pore center.}
-  \label{fig:water_density}
+  \includegraphics[width=\textwidth]{head_group_density_overlay.png}
+  \caption{}\label{fig:head_group_density_overlay}
+  \end{subfigure}
+  \caption{}\label{fig:rdouble_structuring}
   \end{figure}
 
-  %BJC: this may be okay to push to supplemental
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{layered_xy_correlation.png}
-        \caption{Sandwiched, Dry}
-        \label{fig:layered_xy_correlation_comparison}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{layered_solvated_xy_correlation.png}
-        \caption{Sandwiched, Solvated}
-        \label{fig:layered_solvated_xy_correlation}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{offset_xy_correlation.png}
-        \caption{Parallel Displaced, Dry}
-        \label{fig:offset_xy_correlation_comparison}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{offset_solvated_xy_correlation.png}
-        \caption{Sandwiched, Solvated}
-        \label{fig:offset_solvated_xy_correlation}
-  \end{subfigure}
-  \caption{$g(x,y)$ of monomer head groups illustrates how the pores
-	  swell in the presence of water.}~\label{fig:solvated_correlation}
-  \end{figure}
+%  In all cases, water disrupts structuring of the model. When we add water to
+%  the system, the intensity of the reflections decrease. In systems built with 5
+%  wt\% water, R-$\pi$ and R-spots become nearly indistinguishable from R-alkanes.
+%  In systems built with 5 wt\% water, the pore region becomes filled with
+%  water. We plotted the number density of components in this system. As with the 
+%  dry systems, we see a gradual compositional transition from hydrophilic to hydrophobic.  
+%  We see that the pores become a mixture of water molecules and sodium ions (Fig.
+%  \ref{fig:water_density}). We also see that water exists in the tail region which 
+%  may decrease the tail ordering and explain the decrease in intensity of R-spots.
+%  
+%  The membrane swells when we introduce water. The location of maximum head
+%  group density shifts from 0.35 to 0.62 nm and from 0.44 to 0.61 nm in the
+%  parallel displaced and sandwiched configurations respectively. Again, we
+%  observe the existence of ions, head groups and water outside the pore region,
+%  however in the hydrated system, the head groups drift beyond 1.5 nm from the
+%  pore center. In the dry systems, head groups did not wander beyond 1.4 nm from
+%  the pore center. Both observations suggest that water pushes all components
+%  radially outward from the pore center, characteristic of a swelling process.
+%  The plots of $g(x,y)$ for dry and wet systems are compared in
+%  Figure~\ref{fig:solvated_correlation}. They further illustrate how the system
+%  swells in the presence of water. This system is a closer representation
+%  of the H\textsubscript{II} phase which is typically synthesized with ca. 8 wt\%
+%  water. Further investigation of hydrated systems can help unravel the
+%  mechanisms for selective transport in separations of aqueous solutions. 
+%
+%  Water is not necessary to maintain an ordered pore structure. We do not
+%  eliminate the possibility that water is necessary in order to drive
+%  self-assembly, but studying the mechanisms of self-assembly is beyond the
+%  scope of this work. According to our model, once the system has formed the
+%  Col\textsubscript{h} phase, adding water only drives disorder of the pore
+%  structure. In the true equilibrium configuration, if water exists, it is
+%  primarily confined to the pore region where there is no driving force for
+%  aggregation of water molecules. In the case of trace water, water molecules
+%  will be too sparse to form a hydrogen bonding network.
+%
+%  \begin{figure}
+%  \centering 
+%  \begin{subfigure}{0.45\textwidth}
+%        \includegraphics[width=1\linewidth]{offset_solvated_density.png}
+%        \caption{Parallel Displaced}
+%        \label{fig:offset_solvated_density}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%        \includegraphics[width=1\linewidth]{layered_solvated_density.png}
+%        \caption{Sandwiched}
+%        \label{fig:layered_solvated_density}
+%  \end{subfigure}
+%  \caption{Water fills the membrane pores in the parallel displaced (a) and
+%	  sandwiched (b) configurations. Head groups in the sandwiched configuration sit
+%	  closer to the pore center than they do in the parallel displaced configuration.
+%	  Both systems are composed primarily of water close to the pore center.}
+%  \label{fig:water_density}
+%  \end{figure}
+%
+%  %BJC: this may be okay to push to supplemental
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.47\textwidth}
+%        \includegraphics[width=1\linewidth]{layered_xy_correlation.png}
+%        \caption{Sandwiched, Dry}
+%        \label{fig:layered_xy_correlation_comparison}
+%  \end{subfigure}
+%  \begin{subfigure}{0.47\textwidth}
+%        \includegraphics[width=1\linewidth]{layered_solvated_xy_correlation.png}
+%        \caption{Sandwiched, Solvated}
+%        \label{fig:layered_solvated_xy_correlation}
+%  \end{subfigure}
+%  \begin{subfigure}{0.47\textwidth}
+%        \includegraphics[width=1\linewidth]{offset_xy_correlation.png}
+%        \caption{Parallel Displaced, Dry}
+%        \label{fig:offset_xy_correlation_comparison}
+%  \end{subfigure}
+%  \begin{subfigure}{0.47\textwidth}
+%        \includegraphics[width=1\linewidth]{offset_solvated_xy_correlation.png}
+%        \caption{Sandwiched, Solvated}
+%        \label{fig:offset_solvated_xy_correlation}
+%  \end{subfigure}
+%  \caption{$g(x,y)$ of monomer head groups illustrates how the pores
+%	  swell in the presence of water.}~\label{fig:solvated_correlation}
+%  \end{figure}
 
   \subsection{Model Ionic Conductivity Measurements}
+
+  %BJC5: probably should show solvated system measurements
+  % 1 wt % water, parallel displaced, ordered basin
+  % Nernst Einstein : (6.52 +/- 0.04) e-05 S/m
+  % Collective Diffusion : (20.6 +/- 9.8) e-05 S/m
 
@@
 
-  The system's pore spacing is most consistent with experiment when systems
-  are built with 5 columns per pore. The distance between pores increases with the 
-  number of columns per pore. Pores pack closer together in the disordered pore 
-  basin. Systems built with 6 columns per pore in the disordered basin expand in 
-  the z-direction which suggest that it may rearrange to 5 columns per pore long term.
-
-  We have maximized our model's consistency with the experimental WAXS pattern. We show
-  that R-alkanes and R-pores appear where expected. We learned that R-spots is likely 
-  due to ordered alkane chain packing. R-$\pi$ appears at lower q values than experiment
-  because monomer stack too far apart. We found that our model cannot reproduce R-double, 
-  however we have come up with a three different mechanisms that lead to the reflection's
-  appearance. The most likely explanation is that monomers within each column rotate ca.
-  15\degree with respect to their vertically adjacent neighbors so that tails can pack 
-  together more tightly.
+  We achieve maximum structural consistency with experiment, as determined by simulated
+  2D structure factors, when we build our model in the ordered basin parallel displaced
+  configuration with 5 monomer columns per pore and 1 wt\% water. R-alkanes and R-pores
+  appear where expected for the reasons originally predicted. We learned that R-spots
+  is likely due to ordered alkane chain packing. R-$\pi$ appears at lower q values than
+  experiment because monomer stack too far apart. Finally, we observed that our model
+  reproduces R-double only when we add 1 wt\% water to the system. This observation has
+  important implications for the reproducibility of the experimental results from Feng 
+  et al since they claim that their membrane is completely dry.
+
+%  The system's pore spacing is most consistent with experiment when systems
+%  are built with 5 columns per pore. The distance between pores increases with the 
+%  number of columns per pore. Pores pack closer together in the disordered pore 
+%  basin. Systems built with 6 columns per pore in the disordered basin expand in 
+%  the z-direction which suggest that it may rearrange to 5 columns per pore long term.
+
+%  We have maximized our model's consistency with the experimental WAXS pattern. We show
+%  that R-alkanes and R-pores appear where expected. We learned that R-spots is likely 
+%  due to ordered alkane chain packing. R-$\pi$ appears at lower q values than experiment
+%  because monomer stack too far apart. We learned that our model reproduces R-double when
+%  we add 1 wt\% water to the system.
 
@@
   learned that the pores are generally filled with monomer head groups and sodium
-  ions. All systems studied showed a similar distribution of sodium, head groups 
-  and tails, which means we can study solute transport in any of the systems here
-  and extract similar transport mechanisms. We also observed that there is not a 
-  hard partition between hydrophlic and hydrophilic regions, rather there is a 
-  gradient. This finding has raised questions about the nature of size-exclusion separations.
-
-  We learned that we do not need water to create well-defined pore structures.
-  Systems whose pores were filled with varying amounts of water showed a decrease
-  in structuring relative to dry systems. At higher water concentrations, the pores
-  begin to swell, which may be more conducive to transport.
+  ions. All dry systems studied showed a similar distribution of sodium, head groups 
+  and tails while the wet system shows evidence of swelling due to the presence of 
+  water molecules. We also observed that there is not a hard partition between hydrophlic
+  and hydrophobic regions, rather there is a gradient. This finding has raised questions
+  about the nature of size-exclusion separations in systems without a well-defined pore 
+  size.
+
+%  We learned that we do not need water to create well-defined pore structures.
+%  Systems whose pores were filled with varying amounts of water showed a decrease
+%  in structuring relative to dry systems. At higher water concentrations, the pores
+%  begin to swell, which may be more conducive to transport.
 

### 2018-05-25 Ben_Manuscripts/structure_paper/supporting_information.tex
Revisions and new figures

@@
   We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
-  generated using Packmol (\cite{martinez_packmol:_2009}). The input file given to 
-  Packmol is shown below.
+  generated using Packmol \cite{martinez_packmol:_2009} (Figure~\ref{fig:isotropic_box}).
+  The input file given to Packmol is shown below.
+
   \lstset{language=bash}
@@
   box with a volume of 660 $nm^3$, 25 \% larger than those used to create ordered unit
-  cells we studied.
+  cells we studied. We tested systems with semiisotropic and anisotropic pressure 
+  coupling since the shape of the unit cell will likely need to change in order to 
+  accomodate hexagonally packed pores.
 
   We use the nematic order paramter as defined in section~\ref{method:nematic_order} to 
-  observe any progress towards an system ordering.
-
-  %BJC: picture of isotropic box (before and after?)
-  %BJC: plot of nematic order parameter vs. time
+  observe any progress towards system ordering. In both cases, we see that the nematic
+  order parameter stays close to zero for the duration of the simulation time, indicating
+  an isotropic arrangement of head groups (Figure~\ref{fig:nematic_isotropic}). The values
+  are slightly negative since there are only 400 monomers. 
+  Equation~\ref{eqn:nematic_order_parameter} is bounded between -1 and 1, however, with a
+  proper choice of nematic director, measured values will range between 0 and 1. With a 
+  large number of samples, an isotropic system would have an order parameter of 0.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{isotropic_box.png}
+  \caption{}\label{fig:isotropic_box}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{nematic_isotropic.png}
+  \caption{}\label{fig:nematic_isotropic}
+  \end{subfigure}
+  \caption{(a) We created a box of isotropically packed monomers and allowed it to simulate
+  for 100 ns using isotropic and anisotropic pressure coupling. (b) The nematic order 
+  parameter hovers close to zero for the duration of the simulation meaning the system
+  maintains its isotropic alignment.}\label{fig:self_assembly}
+  \end{figure}
 
@@
 
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{carboxylate_dihedral_rb.png}
+  \caption{A potential energy diagram for the dihedral angle about the carbon-carbon bond of
+  a carboxylate group attached to an aromatic ring, using parameters from the generalized amber 
+  forcefield. It is energetically favorable for the carboxylate group to stay in plane with 
+  the aromatic ring. There is a large energy penalty as the dihedral becomes antiparallel to 
+  the plane of the aromatic ring.}\label{fig:carboxylate_dihedral_rb}
+  \end{figure}
+
 \clearpage

### 2018-05-25 HII/Scripts/Diffusivity.py

@@ -105,7 +105,7 @@ def msd_straightforward(x, ndx):
 
 class Diffusivity(object):
 
-    def __init__(self, traj, gro, axis, startfit=0.05, endfit=0.2, residue=False, atoms=[]):
+    def __init__(self, traj, gro, axis, begin=0, startfit=0.05, endfit=0.2, residue=False, atoms=[]):
         """
         Calculate diffusivity from trajectory
         :param traj: unwrapped trajectory (i.e. gmx trjconv with -pbc nojump)
@@ -121,7 +121,7 @@ class Diffusivity(object):
         self.top_location = "%s/../top/topologies" % self.script_location
 
         print('Loading trajectory...', end='', flush=True)
-        t = md.load(traj, top=gro)  # load trajectory
+        t = md.load(traj, top=gro)[begin:]  # load trajectory
         print('Done!')
         self.nT = t.n_frames  # number of frames
         self.time = t.time  # time stamp on each frame
@@ -204,6 +204,7 @@ class Diffusivity(object):
 
             self.yfit, _, self.slope_error, _, A = Poly_fit.poly_fit(self.time[self.startfit:self.endfit],
                                                   self.MSD_average[self.startfit:self.endfit], 1, self.W)
+
             plt.plot(self.time[self.startfit:self.endfit], self.yfit, '--', color='black', label='Linear Fit')
 
             # plt.errorbar(self.time, self.MSD_average, yerr=[self.limits[0, :], self.limits[1, :]],
@@ -222,7 +223,7 @@ class Diffusivity(object):
                 print('Press enter to following prompts to leave as is')
                 self.startfit = float(input("Time to start fit (ns): ") or self.startfit)
                 self.endfit = float(input("Time to stop fit (ns): ") or self.endfit)
-                self.startfit = int(self.startfit / (self.dt/1000.0)) # convert time to index in t.time
+                self.startfit = int(self.startfit / (self.dt/1000.0))  # convert time to index in t.time
                 self.endfit = int(self.endfit / (self.dt/1000.0))
             plt.clf()
 

### 2018-05-25 HII/Scripts/equil.sh

@@ -41,6 +41,7 @@ fi
 # make input files
 ${python} ${DIR}/input.py -b ${BUILD_MON} -l 50 --restraints ${restraint_residue} --temp ${T} -f 50 --genvel yes -c ${start_config}
 # create restrained topology
+
 ${python} ${DIR}/restrain.py -f 1000000 1000000 1000000 -A xyz -g ${start_config} -m ${BUILD_MON} -a ${ring_restraints}
 
 gmx grompp -f em.mdp -p topol.top -c ${start_config} -o em

### 2018-06-08 Ben_Manuscripts/structure_paper/Draft.tex
Draft updates + PMF stuff

@@
   	\centering
-  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png}
+  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png} %BJC5: this needs to be updated
   	\caption{}\label{fig:staggered_rzplot_norestraints} 
-  	%BJC4: needs to be done
   \end{subfigure}
@@
   of the parallel displaced configuration become more diffuse, which is a closer match to 
-  experiment. If water is truly responsible for R-double, then the there is likely
+  experiment. If water is truly responsible for R-double, then there is likely
   between 1 and 2.5 wt\% water absorbed into the membrane. This does not exclude 
@@
 
-  Water causes the monomer head groups to restructure. We confirmed that the reflection is 
-  not caused by the water itself. We removed all water molecules from the trajectory and 
-  showed that R-double is still present in the simulated diffraction pattern 
-  (Figure~\ref{fig:rdouble_nowater}). We also confirmed that the tails are not responsible for
-  R-double. R-double is not present when we remove all atoms except carbon atoms that make
-  up the tails (Figure~\ref{fig:rdouble_tails}). It is clear that interactions between water
-  and head groups causes them to restructure in a way that leads to R-double.
-
+  R-double appears due to the structure of the head groups. We removed the head groups from the
+  trajectory used to produce Figure~\ref{fig:solvation}a in order to produce that shown
+  in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear without the influence of the
+  head groups. Water molecules must play a role in the structuring of the head groups since 
+  R-double does not appear in any dry simulations.
+
+%  Water causes the monomer head groups to restructure.   
+%  We confirmed that the reflection is 
+%  not caused by the water itself. We removed all water molecules from the trajectory and 
+%  showed that R-double is still present in the simulated diffraction pattern 
+%  (Figure~\ref{fig:rdouble_nowater}). We also confirmed that the tails are not responsible for
+%  R-double. R-double is not present when we remove all atoms except carbon atoms that make
+%  up the tails (Figure~\ref{fig:rdouble_tails}). It is clear that interactions between water
+%  and head groups causes them to restructure in a way that leads to R-double.
+
+  % BJC5: This figure may belong in supplemental
   \begin{figure}[!htb]
   \centering
-  \begin{subfigure}{0.32\textwidth}
+  \begin{subfigure}{0.45\textwidth}
   \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
@@
   \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{rdouble_nowater_rzplot.png}
-  \caption{Water removed}\label{fig:rdouble_nowater}
-  \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{rdouble_tails_only_rzplot.png}
-  \caption{Tails only}\label{fig:rdouble_tails}
-  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
+  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
+  \end{subfigure}
+%  \begin{subfigure}{0.32\textwidth}
+%  \includegraphics[width=\textwidth]{rdouble_tails_only_rzplot.png}
+%  \caption{Tails only}\label{fig:rdouble_tails}
+%  \end{subfigure}
   \caption{The structure of the head groups is responsible for the appearance of
-  R-double in (a). Removing water from the trajectory (b) results in a simulated 
-  diffraction pattern nearly identical to that in (a). R-double is not present
-  when we simulate the diffraction pattern of system where only tails are present. 
-  (c)}\label{fig:rdouble_origin}
+  R-double in (a). Removing head groups from the trajectory results in a simulated 
+  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
   \end{figure}
 
-  The appearance of R-double may be due to increased order of the pores. The first
-  peak of the correlation function, $g(z)$, is approximately 30 \% larger in the 
-  solvated versus dry configuration (Figure~\ref{fig:solvated_correlation_overlay}).
-  Based on the peak locations, it is evident that the head groups stack closer 
-  together in the solvated configuration which may play a role in enforcing order.
-  This may be in part due to swelling of the pores. In 
-  Figure~\ref{fig:head_group_density_overlay} there is a clear decrease in 
-  head group density within 0.4 nm of the pore center. Water molecules may swell 
-  the pores and hydrogen bond with monomer head groups, tethering the monomers 
-  closer together. If this is the case, then it implies that R-double has always
-  been at least weakly present in the simulated diffraction patterns, but may 
-  have been buried by noise.
+  When two vertically stacked monomer head groups hydrogen bond with a shared water 
+  molecule, the monomers are drawn closer together (as illustrated in 
+  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows 
+  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
+  with a head group below itself, it will be less likely to share a water molecule 
+  with a head group above it due to steric constraints. The monomer head group above
+  can just as easily share a water molecule with a head group above itself. In this scenario,
+  the centers of each group are 2 times the $\pi$-stacking distance apart which would
+  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
+  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
+  Peaks in the distributions represent the scenario where a monomer head group shares a 
+  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
+  we calculated the discrete fourier transform of the distributions which we used as a rough 
+  indicator of whether the head group arrangement will lead to R-double. We see the 
+  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
+  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.
 
@@
   \centering
+  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
+  % to the floating head groups)
+  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
+  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
+  drawn closer together. Head groups with blue bonds were stacked above those 
+  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
+  \end{figure}
+
+  \begin{figure}[!htb]
+  \centering
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{solvated_correlation_overlay.png}
-  \caption{}\label{fig:solvated_correlation_overlay}
+  \includegraphics[width=\textwidth]{pore_hbonds.png}
+  \caption{}\label{fig:pore_hbonds}
   \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{head_group_density_overlay.png}
-  \caption{}\label{fig:head_group_density_overlay}
-  \end{subfigure}
-  \caption{}\label{fig:rdouble_structuring}
+  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
+  \caption{}\label{fig:pore_hbonds_ft}
+  \end{subfigure}
+  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
+  shared hydrogen bonded water molecule between a monomer head group and that stacked
+  vertically above it. (b) }\label{fig:hbond_quantification}
   \end{figure}
+
+%  The appearance of R-double may be due to increased order of the pores. The first
+%  peak of the correlation function, $g(z)$, is approximately 30 \% larger in the 
+%  solvated versus dry configuration (Figure~\ref{fig:solvated_correlation_overlay}).
+%  Based on the peak locations, it is evident that the head groups stack closer 
+%  together in the solvated configuration which may play a role in enforcing order.
+%  This may be in part due to swelling of the pores. In 
+%  Figure~\ref{fig:head_group_density_overlay} there is a clear decrease in 
+%  head group density within 0.4 nm of the pore center. Water molecules may swell 
+%  the pores and hydrogen bond with monomer head groups, tethering the monomers 
+%  closer together. If this is the case, then it implies that R-double has always
+%  been at least weakly present in the simulated diffraction patterns, but may 
+%  have been buried by noise.
+% 
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{solvated_correlation_overlay.png}
+%  \caption{}\label{fig:solvated_correlation_overlay}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{head_group_density_overlay.png}
+%  \caption{}\label{fig:head_group_density_overlay}
+%  \end{subfigure}
+%  \caption{}\label{fig:rdouble_structuring}
+%  \end{figure}
 
@@
 
-  %BJC5: probably should show solvated system measurements
-  % 1 wt % water, parallel displaced, ordered basin
-  % Nernst Einstein : (6.52 +/- 0.04) e-05 S/m
-  % Collective Diffusion : (20.6 +/- 9.8) e-05 S/m
+  %BJC5: which system should I study here? I wrote this before the solvated
+  % system showed R-double. It might make sense to study the solvated system for ionic
+  % conductivity and cross-linking.
 

### 2018-06-08 HII/Scripts/setup_umbrella_configs.py

@@ -1,9 +1,10 @@
 #!/usr/bin/env python
 
 import numpy as np
-import mdtraj as md
 import place_solutes
 import argparse
+import genmdp
+import os
 
 
 def initialize():
@@ -17,25 +18,112 @@ def initialize():
     parser.add_argument('-l', '--layers', default=20, type=int, help='number of layers in initial configuration')
     parser.add_argument('-p', '--pores', default=4, type=int, help='number of pores to add solutes to')
     parser.add_argument('-frac', default=0.5, type=float, help='Fraction into membrane to start placing solutes')
-    parser.add_argument('-o', '--output', default='solvated', help='Prefix to name of output coordinate files')
+    parser.add_argument('-T', '--temp', default=300, type=float, help='Temperature to run simulations at')
+    parser.add_argument('-o', '--output', default='umbrella')
+    parser.add_argument('-r', '--ref', default=18, help='Layer number for reference com in each pore. The default value'
+                        'of 18 will calculate the center of mass in each pore defined by the monomers that make up the'
+                        '18th layer.')
+    parser.add_argument('-L', '--sim_length', default=10000, type=int, help='Simulation length for each umbrella (ps)')
+    parser.add_argument('-f', '--frames', default=100, type=int, help='Number of simulation frames to record. Will '
+                        'determine nstxout, nstvout, and nstfout. Which means they will have the same value')
+    parser.add_argument('-dt', default=0.002, type=float, help='Simulation time step (ps)')
 
     args = parser.parse_args()
 
     return args
 
 
+def create_pull_groups(system, solute, layer, nlayers, pores, ref_resname='HII', out='index.ndx'):
+    """
+    :param system: object created by place_solutes.Solvent(). Will be used to make reference com groups
+    :param solute: object created by place_solutes.Solute(). Will become a pull group
+    :param layer: layer number which will be used as reference for com, starting at 1 (int)
+    :param nlayers: number of layers per pore (int)
+    :param pores: number of pores in system (int)
+    :param resname: name of residue that will be restrained
+    :param ref_resname: name of reference residue, some of whose atoms will define reference center of mass
+    :param out: name of output index file
+    :return: names of pull groups
+
[…]

### 2018-06-11 Ben_Manuscripts/structure_paper/Draft.tex
comments.

@@
   transport within these nanopores.
-
+  %MRS7: some more of the conclusions should be in the abstract.  'introduction' just raises questions, but 
+  %'abstract' should give a executive-level summary of the answers.
   \end{abstract}
@@
 
-  A highly selective membrane would be useful for the recovery of valuable
+  More highly selective membranes would be extremely useful for the recovery of valuable
   products from complex aqueous and organic solutions.  For example, flowback
@@
 
+  %MRS: abstract seems a bit limited, describe more generally (and
+  briefly!) other things selective membranes are good for. The paper is primarily about selective membranes, not fracking water.  It seems out of balance to be talking about only one application.
+
 %  The permeability-selectivity tradeoff is a well-known problem in the membrane
@@
 % work for this purpose. But one paragraph is enough.
-% BJC5: added back below paragraph
-  Current commercial RO and NF membranes suffer limitations to there selectivity 
+% BJC5: added back below paragraph.  
+% MRS7: Do a pass for clarity at the sentence level.  For example ``degree of stochasticity'' is vague.
+  Current commercial RO and NF membranes suffer limitations to their selectivity 
   which is inherent to their fabrication. Although scalable, each of these two types
@@
   \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane pores
-  are uniform in size. Since LLC membranes lack a pore size distribution, they
+  are uniform in size because they are self-assembled. 
+  Since LLC membranes lack a pore size distribution, they
   inherently exhibit high selectivity due to their strict molecular weight
@@
   \end{subfigure}
-%MRS5: not sure Q should be in here.
+%MRS5: not sure Q should be in here.  Could cut length by removing some of the detail about Q phase, since it 
+isn't discussed in the paper. 
   \caption{The choice of LLC monomer and solvent leads to different accessible liquid
@@
         represent the interface between the hydrophilic and hydrophobic regions of the unit
-        cell. As pictured, we assume that each region occupies an equal volume. The
+        cell. 
+        %MRS7: not needed
+        %As pictured, we assume that each region occupies an equal volume. 
+        The
         monomer shown in (b) will form the hexagonal columnar phase
@@
   systems have been macroscopic models that likely do not adequately describe
-  transport at these length scales \cite{hatakeyama_water_2011}. It will be
-  challenging to efficiently narrow down the large design space in a laboratory
-  setting without a robust model.
-
+  transport at these length scales \cite{hatakeyama_water_2011}. 
+  %MRS7: maybe a pass at this?
+  Modeling with molecular detail could provide sufficient information about the mechanisms 
+  and chemical features to better inform experimental design of similar nanostructured membranes. 
+  %It will be
+  %challenging to efficiently narrow down the large design space in a laboratory
+  %setting without a robust model.
+
+  %MRS7: changing future tense to present tense here.
   A molecular-level understanding of LLC polymer membrane structure, enabled by
@@
   membranes. A good molecular model should incorporate a detailed picture of the
-  nanoscopic pore structure which will be crucial to understanding the role of
+  nanoscopic pore structure which is crucial to understanding the role of
   monomer structure in solute transport and membrane design. Models resulting
-  from molecular dynamics simulations will provide the required level of detail
+  from molecular dynamics simulations can provide the required level of detail
   (Fig. \ref{fig:detail}), assuming the force fields are sufficiently accurate.
@@
 	\end{subfigure}
-    \caption{One can only speculate about solute behavior inside the membrane
-	  pores based on the previously established picture of the pore structure (a). 
-      We use a detailed molecular model in order to appropriately model the pore's
+    %MRS7: Adjusted the phrasing
+    \caption{(a) Previous understanding of the pores are essentially speculations based on limited chemical and experimental data.
+(b) We use a detailed molecular model in this paper in order to appropriately model the pore's
       complex architecture which is crucial to understanding the mechanism of solute
-	  transport (b). The head group region is colored blue and the tail region is
-	  colored cyan in both representations. This image was generated from the molecular
-	  simulations run for this paper.}~\label{fig:detail}
+	  transport. In both pictures, the head group region is colored blue and the tail region is
+	  colored cyan. 
+          %MRS7: don't think this is needed.
+          %This image was generated from the molecular simulations run for this paper.
+          }~\label{fig:detail}
   \end{figure}
 
-  Here we develop a molecular model of the Col\textsubscript{h} assembly formed by
+  %Here 
+  In this paper,
+   we develop a molecular model of the Col\textsubscript{h} assembly formed by
   Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
@@
   characterization of the fully aligned state, including 2D wide-angle X-ray
-  scattering (WAXS) patterns (Figure\ref{fig:WAXS}) which are useful for reconstructing 
+  scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
   structural data. We will use this Col\textsubscript{h} model in order to build an 
@@
         \end{subfigure}
-	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
+        %MRS7: picture says R-helix still.
+	\caption{(a) (Reproduced from \citenum{feng_thin_2016}) The repeat spacing
 		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
@@
 
+        %MRS7: is this really a liquid crystalline system, even if it is made of liquid crystal monomers? Should we say
+        % in many liquid crystal systems?
  	We are careful to avoid the term 'layers' since a liquid crystalline system has, by 
@@
  	hexagonal array of pores (xy plane) and short range correlations in the z-direction.
- 	We will use our atomistic molecular model to study how the system's structure is 
- 	effected by the density of monomers surrounding each pore's hydrophilic core.
+        %MRS7: look carefully at tenses.  Don't describe the research in future tense. 
+        % if it's describing your presentation of the research in the paper , use present tense. 
+        % If it's describing something you did, use past tense. I changed some of them, but not all.
+ 	%We will use 
+        In this study, we use
+        our atomistic molecular model to study how the system's structure is 
+        affected
+ 	%effected 
+        by the density of monomers surrounding each pore's hydrophilic core.
 
@@
 
-	On the short timescales accessible to MD, we observe distinct metastable configurations
+	On the short timescales accessible to MD
+        %MRS7: added the following to make it clear the scale of the effort
+        (even the 100's of nanoseconds of simulation peformed here are short compared to experimental timescales),
+        we observe distinct metastable configurations
 	which depend on starting configuration. We simulated XRD patterns of our system and 
-	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS} so that we ensure our
+	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS}) so that we ensure our
 	model creates a nanoscopic chemical environment maximally consistent with experiment within 
@@
   method of \texttt{molcharge} shipped with QUACPAC from Openeye Scientific
-  Software. We ran all molecular dynamics simulations using Gromacs 2016
+  Software. We ran all molecular dynamics simulations using GROMACS 2016
   \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
@@
   X-ray diffraction patterns. %This point will be explained in more detail later.
+  %MRS7: refer to supporting information (if it's there) for more discussion on stability as a function of height?
 
@@
   \AA. We briefly explored a third system with an initial spacing of 10
-  \AA, however it shows non-physical behavior which is detailed in the 
+  \AA. However this spacing yields non-physical behavior which is detailed in the 
   Supporting Information, section S-\ref{S-section:initial_dbwl}.
@@
   \subsection{Equilibration}
-
+  %MRS7: could put this mostly in supporting. 
   We developed equilibration schemes to create dry and wet configurations. Both
@@
   \cite{chodera_simple_2016,shirts_statistically_2008}. Simulations of 400 ns
+  %MRS7: is there a typical total time as well?
   give at least 50 ns of equilibrated simulation trajectory.
@@
   the membrane plane). We averaged all 1D slices in the z-direction of the full 3D 
-  correlation function within 2.1~\AA~of $(x, y)=(0, 0)$. We chose 2.1 \AA as a crude 
+  correlation function within 2.1~\AA~of $(x, y)=(0, 0)$. We chose 2.1 \AA~as a crude 
   approximation of the radius of the phenyl ring plane. 
@@
   We also used $g(z)$ to calculate the equilibrated vertical stacking distance between
-  monomers, $\mathit{d}_equil$. 
+  monomers, $d_{equil}$. 
   %BJC5: in case there is an criticism of this method
@@
   \begin{equation}
-  	1 - Acos(\frac{2\pi}{\mathit{d}_{equil}}z + B)e^{-z/L}
+  	1 - A\cos\left(\frac{2\pi}{\mathit{d}_{equil}}z + B\right)e^{-z/L}
   	\label{eqn:decaying_sinusoid}
@@
 
-  In order to fully match synthetic procedures, we created a cross-linking
-  algorithm that one can apply to equilibrated structures. The purpose of
+  %In order to fully match synthetic procedures, 
+  In order to maximally match the experimental membrane synthesis process
+  we created a cross-linking
+  algorithm that one can apply to equilibrated structures. 
+  %MRS7: I think the main purpose of crosslinking is mechanical stability.
+  The purpose of
   cross-linking is to maintain macroscopic alignment of the crystalline domains,
@@
   concerned with replicating the kinetics of the reaction, but instead emphasize
+  %MRS7: Since the initial structure isn't that well captured by experiment, then it's probably
+  % better to say that we are interested in knowing how much and in why way cross-linking modulates the structure. 
   the consistency of the final structure with experimental structural data.
@@
   %BJC5: perhaps this paragraph should be moved to supporting info.
+  %MRS7: probably?  Describing the _idea_ of the procedure can be in
+  %main paper, but perhaps more details of the procedure in the supporting info.
+
   We developed the algorithm based on the known reaction mechanism.
@@
   the measured equilibrated pore-to-pore distances. To discern the composition of
-  the monomer layers, addressing question (\ref{point:monomernum}), we ran
+  the monomer layers, addressing question \ref{point:monomernum}, we ran
   simulations of systems created with 4--8 columns per pore. We built systems in both
@@
   frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
-  we are trying to match. In the limit of infinite simulation time, all systems will converge to
-  a single equilibrium configuration. For simplicity, we will group the systems studied here into
+  we are trying to match. In the limit of infinite simulation time, all systems will in theory converge to
+  a single equilibrium configuration, but that time is far beyond the 100's of nanosecond simulated here. 
+  For simplicity, we 
+  %MRS7: tenses
+  %will group the systems studied here into
   the ordered and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
@@
   The reason for these names will become clearer as we progress through our analysis.
-
+  %MRS7: maybe above say where (i.e.
+what section) it will become clear?
+Or possibly describe them here by order parameter instead of by starting distance, and state the correlation between starting distance and order parameter.
 %    All systems tested are at least metastable on the timescales studied here, however not all 
@@
   %BJC5: thesis needs rewording.
+  %MRS7: probably, since the disorered - 6 are close to the experimental distances.  Is it accurate to say
+  %that they don't have the experimental structural features? 
   Disordered basin systems built with 6 columns-per-pore are not compact in the z-direction.
@@
 	\includegraphics[width=\linewidth]{p2p.png}
+        %MRS7: need to deal with the fact that layer-6, more disordered are within error of 4.12
+        %MRS7: I think the answer is that the equilibrated distance is much bigger. you talk about the INITIAL distance being bigger, but I think you also need to emphasize that it stays there.
 	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
@@
   \includegraphics[width=\textwidth]{box_dimensions.png}
+  %MRS7: not really clear from the caption why this is shown.
   \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5~\AA~$), the unit cell
@@
   basins. We extended each simulation by 100 ns in order to get more equilibrated 
-  data. We generated simulated patterns using the extended simulation trajectories.
+  data. 
+  %MRS7: sentence above reads strangely. Was ``more'' sufficient? what criteria was used to stop at 10?
+We generated simulated patterns using the extended simulation trajectories.
   The patterns for all structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
@@
   section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
-  to sample enough independent configurations. Increasing the number of trajectory frames
+  to sample enough 
+  truly
+ independent configurations. 
+ %MRS7: two things going on - they are not smooth because of lack of sampling WITHIN the metastable basin (somewhere in there mention angle averaging leads to less data at q=0 than anywhere else, but this is separate from being truly independent, which would mean totally converged in the equilibrium ensemble (i.e.
+reaching a single equilibrium ensemble in the >miliseconds timescale)  Increasing the number of trajectory frames
   used to simulate the structure factor within a given interval of time does not offer 
   any improvement.
-
+%MRS7: not sure what you mean above. Increasing the frequency of frames used? 
   %BJC5: put figure letters in upper left hand corner of each pattern.
@@
 	\end{subfigure}	
+        %MRS7: be consistent on capitalization
 	\caption{Simulated X-ray diffraction patterns show some qualitative agreement with 
@@
 	In all cases, R-double is not present.}~\label{fig:XRDsim} 
+        %MRS7: may need to make clearer the differences between the simulated structures. I think its worth pointing out
+        %that although rdouble isn't there, for the more structured ones, there is a 7.4 band, even if it disappears at q=0.
   \end{figure}
@@
   %BJC5: Bold font is caused by achemso document type
-
+  %MRS7: huh.
   There are clear differences between simulated and experimental results that must be addressed
-  and justified. We will explore the origin of each experimental reflection and form structural
+  and justified. We will explore 
+  the 
+  %MRS7: possible or likely origin
+  origin of each experimental reflection and form structural
   hypotheses related to their appearance in our simulated patterns. Specifically, we want answer:  
@@
   The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3). R-double is still
-  not present. We will use this configuration to more thoroughly explore the origin of R-spots.
+  not present. We will use 
+  %MRS7: be more specific when you say ``this configuration'' Just the simulation at 280K? The system is a set of configuraitons. 
+this configuration to more thoroughly explore the origin of R-spots.
 
@@
   In this case, the simulated R-spots is more intense than experiment.}
+  %MRS7: slightly more than experiment; 1.3 and 1.5 are pretty comparable given the scale of other things.
+  %MRS7: a and b aren't explained. 
   \end{figure}
 
+%MRS7: maybe ``evidence strongly suggests that?''  
   The R-spots signal is not a result of alkane chain tilt. Previous literature
@@
 
+%MRS7: a thought - moving some of figures 10,11,12 together with some subfigures, since they all communicate the same idea.
+%11a is probably unneeded.
   \begin{figure}[!htb]
@@
 
+%MRS7: couple -> ``two main''?
+%MRS7: what is the purpose of this paragraph?  I think most people would know why a lower T simulation would be more ordered (though the degree is not known).
   There are a couple reasons why we see stronger ordered chain packing at 280 K compared to
@@
   		may not correctly model the behavior of the tails at 300 K (citation?).
+                % look for papers on protien folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
   		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
@@
 
+%MRS7: discrepancies between experimental and simulated R-\pi?  
   \subsubsection{Discrepancies between R-$\pi$}\label{section:rpi}
 
+%MRS7: not a strong thesis sentence. 
   We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
@@
   Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
-  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $\mathit{d}_{equil}$ \\ 
+  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
   Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
@@
 
+%MRS7: other hypothesis about stacking that comes from Matt's implications is that it may have to do with
+%tail entropy, and for some reason ours is frozen in a configuration that is a bit too far apart. I see you talk about this later, but might need to be brought up again.
+
   The correlation length between stacked monomer head groups of the ordered systems also show
@@
   since the peak heights do not decay significantly. 
+%MRS7: perhaps ``do not show clear patters than can easily be fit to exponential decay?''
   %The amount of noise in the correlation function and the lack of an initial peak suggests that 
@@
 
+  %MRS7: question - pushing Matt on this, he seemed to imply that the high value of the peaks indicated large
+  %LOCAL ordering, and that defects/misaligned pores would give rise to BROADENING, but wouldn't change the 
+  %intensity of the peaks that much.  If so, this isn't a great explanation. 
   The simulated intensity of R-$\pi$ is also more intense than experiment because our system
@@
 
+%MRS7: is this still true with water hydrogen information? do you need to clarify dry?
   There is no way to produce R-double without a more complex initial configuration. We 
-  calculated the structure factor of simple systems that mimic the parallel
+  calculated the structure factor of simple systems 
+%MRS7: a little more detail, e.g. simple idealized systems with points representing monomer head groups 
+that mimic the parallel''.  Also, is ``neither'' correct? Did you do a few variants?
   displaced and sandwiched configurations. Neither give rise to R-double. 
@@
   physical sense.
-
+%MRS7: above: vague.  Define ``this problem''. Move ``speculate'' idea to next paragraph, since that describes the speculation?  
   We can produce R-double if our initial configuration contains alternating parallel and
@@
   configuration like this. Our forcefield causes our system to tend towards uniformly spaced
-  layers. As expected, simulations of this type of system are only stable if position restraints
+  layers. 
+  %As expected
+  Simulations of 
+  %this type of system 
+  unevenly spaced systems are only stable if position restraints
   are applied to heavy atoms of the phenyl rings.
@@
   %BJC5: this section may fit better after the next one?
-
+  %MRS7: yes, put it after water structuring.
   We observe unusually slow dynamics in our system relative to other liquid crysal
+  %MRS7: are columnar liquid crystals the right comparison? Are these stickier? One could imagine that 
+  % energetic considerations in the LLCs smush them tighter together, which makes it harder for them to reorient. 
+  % in which case ours aren't atypical, but just not simulated long enough. 
   systems. Typical diffusion constants for columnar liquid crystals have been reported
@@
 
+%MRS5: let's talk about the implications of this (above); might want to move some of this into the SI.
+
   \begin{figure}[!htb]
@@
   \subsection{Chemical composition of pore columns}
-
+  %MRS7: is ``structure'' also a good word to put here? 
   We are most interested in the composition of the pores since we would like to study
@@
   for a diagram). We averaged the histograms over at least 50 ns of equilibrated trajectory.
+
+  %MRS7: this section reads a little bit as ``and then, and
+  %then''. Think how to make it more focused on core ideas to communicate.
 
@@
   fit through. We leave these investigations for a future study.
+  %MRS7: or could say that the size could be different depending on the the nature of the molecle. Could bring up
+  %Sarah's results with different selectivity of molecules about the same size.
 
@@
   observe how this changes when water is added to the system.
-
+  %MRS7: above: may impede compared to what?
+
+  %MRS7: 
   In general, the composition of each region, particulary the pore region, is 
@@
 
+  %MRS7: generally good data, we should talk about how to tighten it up. For example, thesis shouldn't be 
+  % a history of what we did. 
   We explored the effect of water on pore structure, addressing question
@@
   of trace water concentration in these membranes so we tested a range of water
-  concentrations from 1 to 5 percent. Figure~\ref{fig:solvation} shows the simulated
+  concentrations from 1\% to 5\%. Figure~\ref{fig:solvation} shows the simulated
   diffraction patterns resulting from each configuration.
@@
 	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
-	of water only increase discrepancies with experiment.}%
+	of water increase discrepancies with experiment %MRS7:by increasing disorder?}%
   \label{fig:solvation}
@@
 
-  The addition of water allows R-double to appear. When we add 1 wt\% water to the 
+  The addition of water %allows 
+  results in R-double to transiently appear. When we add 1 wt\% water to the 
   parallel displaced configuration, R-double becomes visible (Figure~\ref{fig:rdouble_offset}). 
@@
   experiment. If water is truly responsible for R-double, then there is likely
-  between 1 and 2.5 wt\% water absorbed into the membrane. This does not exclude 
+  between 1 and 2.5 wt\% water absorbed into the membrane. 
+%MRS7: this is limited by the force field and strength of hydrogen bonding. ``is likely'' is strong.
+This does not exclude 
   possible contributions from the motifs discussed in section~\ref{section:rdouble}. Water
@@
 
+%MRS7: should this be first in the section as motivation.
   The systems studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} were not truly
@@
 
+%MRS7: probably want to say that this is a likely mechanism, if it can
+%occur with the given forcefield, since we had a hard time identifying any others. A more realistic forcefield
+% may make the effect stronger.
+
   \begin{figure}[!htb]
@@
 
+  %MRS7: hmm. Good question. Probably, as long as it's pretty straightforward. For diffusion, you can do just one calculation, and 
+  put the alternate method in SI (you can mention you did it, i.e. we did X, it was noiser, but agreed within data (see SI). 
   We used equilibrated systems in the ordered pore basin to calculate ionic 

### 2018-06-11 Ben_Manuscripts/structure_paper/Draft.tex
More comments.

@@
   %MRS7: this section reads a little bit as ``and then, and
-  %then''. Think how to make it more focused on core ideas to communicate.
-
+  %then''. Think how to make it more focused on core ideas to communicate. Thes is they are all about the same. Perhaps should be the beginning of the section?
+
+  %MRS7: rephrase? Partition implies more abrupt.
   There is a partition between the hydrophobic and hydrophilic regions, however
@@
 
-  %MRS7: 
   In general, the composition of each region, particulary the pore region, is 
@@
 % line is thickest. That way, when the outlines overlap, you can see the ones in front.
+%MRS7: looks weird, though - we should discuss more. Maybe just draw the tops of the histograms, and don't fill them in?
+%MRS7: maybe do as three figures across?
   \begin{figure}[!htb]
@@
   \end{subfigure}
+  %MRS7: lead with ``pretty much the same''
   \caption{In all cases, the component radial distribution functions exhibit a
@@
   \end{subfigure}
+  %MRS7: add a bit more explanation - no description of discrete FT.
   \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
@@
 
-  %MRS7: hmm. Good question. Probably, as long as it's pretty straightforward. For diffusion, you can do just one calculation, and 
-  put the alternate method in SI (you can mention you did it, i.e. we did X, it was noiser, but agreed within data (see SI). 
+  %MRS7: hmm.
+Good question.
+Probably, as long as it's pretty straightforward.
+For diffusion, you can do just one calculation, and put the alternate method in SI (you can mention you did it, i.e.
+we did X, it was noiser, but agreed within data (see SI).
   We used equilibrated systems in the ordered pore basin to calculate ionic 
@@
   displaced configurations in the ordered pore basin. We allowed the crosslinking
-  algorithm to propagate until greater than 90 \% of vinyl groups were either involved
+  algorithm to propagate until greater than 90\% of vinyl groups were either involved
   in a crosslinking reaction or were terminated. See section S\ref{S-section:xlink}
@@
   values of crosslinked configurations fall within uncertainty of their un-crosslinked
-  counterparts. The correlation length decreases in both systems, but is most 
-  pronounced in the parallel displaced system.
+  counterparts. The correlation length decreases in both systems, 
+  %MRS7: from what to what?
+but is most pronounced in the parallel displaced system.
 

### 2018-06-12 Ben_Manuscripts/structure_paper/Draft.tex
draft updates

@@
 \SectionNumbersOn
-
-%\makeatletter
-%\newcommand*{\addFileDependency}[1]{% argument=file name and extension
-%  \typeout{(#1)}
-%  \@addtofilelist{#1}
-%  \IfFileExists{#1}{}{\typeout{No file #1.}}
-%}
-%\makeatother
-% 
-%\newcommand*{\myexternaldocument}[1]{%
-%    \externaldocument{#1}%
-%    \addFileDependency{#1.tex}%
-%    \addFileDependency{#1.aux}%
-%}
 
@@
   selective separations. In this work, we develop an atomistic molecular model
-  of an LLC membrane. We show that our model is maximally consistent with
-  experimental observations by comparing simulated X-ray Diffraction (XRD)
-  patterns and calculated ionic conductivity to their experimental counterparts.
-  We explore, in depth, the composition and structure of the nanopores in order
-  to give insights that are not easily accessible to experimentalists.  The
-  clearer picture of the nanoscopic structure of these membranes provided in this
-  study will enable a better understanding of the mechanisms of small molecule
-  transport within these nanopores.
-  %MRS7: some more of the conclusions should be in the abstract.  'introduction' just raises questions, but 
-  %'abstract' should give a executive-level summary of the answers.
+  of an experimentally characterized LLC membrane. While it is relatively 
+  straightforward to create a stable hexagonal phase model, we demonstrate that 
+  closely reproducing the experimental pore structure requires a carefully 
+  constructed initial configuration in order to avoid falling into a metastable
+  basin. We use simulated X-ray Diffraction (XRD) patterns in order to ensure 
+  maximum consistency between our structures and experiment. We show that pores 
+  are likely composed of 5 columns of stacked LLC monomers which surround each
+  hydrophilic core. Although this system has been reported as dry, we show that
+  small amounts of water are necessary to fully reproduce the experimental XRD
+  pattern due to asymmetries introduced by hydrogen bonds between monomer head
+  groups and water molecules. We explore, in depth, the composition and 
+  structure of the nanopores and reveal that there exists a composition gradient
+  rather than a hard partition between the hydrophilic and hydrophobic regions.
+  The clearer picture of the nanoscopic structure of these membranes provided in
+  this study will enable a better understanding of the mechanisms of small 
+  molecule transport within these nanopores.
+
   \end{abstract}
@@
 
-  %MRS: abstract seems a bit limited, describe more generally (and
-  briefly!) other things selective membranes are good for. The paper is primarily about selective membranes, not fracking water.  It seems out of balance to be talking about only one application.
+  % MRS: abstract seems a bit limited, describe more generally (and
+  % briefly!) other things selective membranes are good for. The paper is primarily about selective membranes, not fracking water.  
+  % It seems out of       balance to be talking about only one application.
 
@@
 
-  The feasibility of LLC membranes has been demonstrated using LLCs that form
-  the type 1 bicontinuous cubic (Q\textsubscript{I})
+  The feasibility of nanostructured LLC membranes for selective separations has been
+  demonstrated using LLCs that form the type 1 bicontinuous cubic (Q\textsubscript{I})
   \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
@@
 
-  The H\textsubscript{II} phase pore geometry is has a higher theoretical capacity
+  The H\textsubscript{II} phase pore geometry has a higher theoretical capacity
   for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
@@
   literature, has been referred to as the Col\textsubscript{h} thermotropic
-  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}). The most
-  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
-  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
+  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}). 
+  % BJC6: maybe not a necessary detail
+%  The most
+%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
+%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
   Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
@@
 
-  % BJC: I like this figure, but I don't know if it is necessary in the main body. i  % Maybe move to supplemental. Thoughts?
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-        \centering
-        \includegraphics[trim=-2cm 0 0 0, clip, height=4.5cm]{Dibrpyr14.eps}
-        \includegraphics[height=4.5cm]{bcc_phases.png}
-        \caption{}\label{fig:bcc_phases}
-  \end{subfigure}
-  \hspace{1cm}
-  \begin{subfigure}{0.45\textwidth}
-        \centering
-        \includegraphics[trim=0 -0.5cm 0 -0.5cm, clip, height=4.5cm]{NaGA3C11.eps}
-        \includegraphics[height=4.5cm]{hexagonal_packing.png}
-        \caption{}\label{fig:hII_phase}
-  \end{subfigure}
-%MRS5: not sure Q should be in here.  Could cut length by removing some of the detail about Q phase, since it 
-isn't discussed in the paper. 
-  \caption{The choice of LLC monomer and solvent leads to different accessible liquid
-        crystalline phases. The monomer shown in (a) forms the Q\textsubscript{I} phase
-        in either the Ia3d (left) or Pn3m (right) space group. The surfaces shown
-        represent the interface between the hydrophilic and hydrophobic regions of the unit
-        cell. 
-        %MRS7: not needed
-        %As pictured, we assume that each region occupies an equal volume. 
-        The
-        monomer shown in (b) will form the hexagonal columnar phase
-        (H\textsubscript{II} in the presence of water or Col\textsubscript{h} when no
-         water is present) The blue region represent the hydrophilic pores while the cyan region represents the surrounding hydrophobic monomer tails.}\label{fig:bcc_v_hII}
-  \end{figure}
+%  % BJC: I like this figure, but I don't know if it is necessary in the main body. i  % Maybe move to supplemental. Thoughts?
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%        \centering
+%        \includegraphics[trim=-2cm 0 0 0, clip, height=4.5cm]{Dibrpyr14.eps}
+%        \includegraphics[height=4.5cm]{bcc_phases.png}
+%        \caption{}\label{fig:bcc_phases}
+%  \end{subfigure}
+%  \hspace{1cm}
+%  \begin{subfigure}{0.45\textwidth}
+%        \centering
+%        \includegraphics[trim=0 -0.5cm 0 -0.5cm, clip, height=4.5cm]{NaGA3C11.eps}
+%        \includegraphics[height=4.5cm]{hexagonal_packing.png}
+%        \caption{}\label{fig:hII_phase}
+%  \end{subfigure}
+%%MRS5: not sure Q should be in here.  Could cut length by removing some of the detail about Q phase, since it 
+%%isn't discussed in the paper. 
+%  \caption{The choice of LLC monomer and solvent leads to different accessible liquid
+%        crystalline phases. The monomer shown in (a) forms the Q\textsubscript{I} phase
+%        in either the Ia3d (left) or Pn3m (right) space group. The surfaces shown
+%        represent the interface between the hydrophilic and hydrophobic regions of the unit
+%        cell. 
+%        %MRS7: not needed
+%        %As pictured, we assume that each region occupies an equal volume. 
+%        The
+%        monomer shown in (b) will form the hexagonal columnar phase
+%        (H\textsubscript{II} in the presence of water or Col\textsubscript{h} when no
+%         water is present) The blue region represent the hydrophilic pores while the cyan region represents the surrounding hydrophobic monomer tails.}\label{fig:bcc_v_hII}
+%  \end{figure}
 
@@
 
-%MRS5: not a strong thesis.  Why has it been revived?  The reasons for that would be a better thesis.
   Recently, researchers have learned how to macroscopically align the hexagonal
@@
 	\end{subfigure}
-    %MRS7: Adjusted the phrasing
-    \caption{(a) Previous understanding of the pores are essentially speculations based on limited chemical and experimental data.
-(b) We use a detailed molecular model in this paper in order to appropriately model the pore's
-      complex architecture which is crucial to understanding the mechanism of solute
-	  transport. In both pictures, the head group region is colored blue and the tail region is
-	  colored cyan. 
-          %MRS7: don't think this is needed.
-          %This image was generated from the molecular simulations run for this paper.
-          }~\label{fig:detail}
+    \caption{(a) Previous understanding of the pores are essentially speculations 
+    based on limited chemical and experimental data. (b) We use a detailed molecular 
+    model in this paper in order to appropriately model the pore's complex architecture
+    which is crucial to understanding the mechanism of solute transport. In both 
+    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
   \end{figure}
 
-  %Here 
-  In this paper,
-   we develop a molecular model of the Col\textsubscript{h} assembly formed by
-  Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
+  In this paper, we develop a molecular model of the Col\textsubscript{h} assembly 
+  formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
   phase is a simpler starting point. The system has no water which will allow us
@@
     % in many liquid crystal systems?
- 	We are careful to avoid the term 'layers' since a liquid crystalline system has, by 
- 	definition, long range order in 1 or 2 spatial dimensions and short range order in 	
+    %BJC5: changed to 'many liquid crystalline systems'
+ 	We are careful to avoid the term 'layers' since many liquid crystalline systems
+ 	have long range order in 1 or 2 spatial dimensions and short range order in 	
  	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
@@
  	%We will use 
-        In this study, we use
-        our atomistic molecular model to study how the system's structure is 
-        affected
- 	%effected 
-        by the density of monomers surrounding each pore's hydrophilic core.
+    In this study, we use our atomistic molecular model to study how the system's structure is 
+    affected by the density of monomers surrounding each pore's hydrophilic core.
 
@@
 
-	On the short timescales accessible to MD
-        %MRS7: added the following to make it clear the scale of the effort
-        (even the 100's of nanoseconds of simulation peformed here are short compared to experimental timescales),
-        we observe distinct metastable configurations
-	which depend on starting configuration. We simulated XRD patterns of our system and 
+	On the short timescales accessible to MD (even the 100's of nanoseconds of simulation 
+	peformed here are short compared to experimental timescales), we observe distinct metastable
+	configurations which depend on starting configuration. We simulated XRD patterns of our system and 
 	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS}) so that we ensure our
@@
   \texttt{pymbar.timeseries.detectEquilibration}, to the time series
-  \cite{chodera_simple_2016,shirts_statistically_2008}. Simulations of 400 ns
-  %MRS7: is there a typical total time as well?
-  give at least 50 ns of equilibrated simulation trajectory.
+  \cite{chodera_simple_2016,shirts_statistically_2008}. Typically, the pore-to-pore
+  distance equilibrates between 200 and 350 ns. We used data collected after 
+  equilibration to do all subsequent analysis.
 
@@
 
-  \subsubsection{\textit{Simulated structure factor calculations}}
+  \subsubsection{\textit{Simulated structure factor calculations}}\label{method:xrd}
 
@@
 
-  We calculated ionic conductivity using two different methods for robustness.
-  The Nernst-Einstein relation, relates the DC ionic conductivity, $\sigma$, to ion
-  diffusivity, $D$, concentration, $C$, ion charge, $q$, the Boltzmann constant,
-  $k_b$, and temperature, $T$: 
+  We calculated ionic conductivity using the Nernst-Einstein relationship, which 
+  relates the DC ionic conductivity, $\sigma$, to ion diffusivity, $D$, 
+  concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
+  temperature, $T$: 
   \begin{equation}
@@
   measured ion concentration with respect to the volume of the entire unit cell.
-  The second method, termed the Collective Diffusion model, measures the
-  movement of the collective variable, Q, which is defined as the amount of
-  charge transfer through the system and can be thought to represent the center
-  of charge of the system. The conductance, $\gamma$, of the system can be
-  calculated as:
-  \begin{equation}
-	 \gamma = \dfrac{D_Q}{k_b T} 
-	\label{eqn:collective_diffusion}
-  \end{equation}
-  We convert the resulting value to ionic conductivity by multiplying by
-  channel length and dividing by the membrane cross sectional area. $D_Q$ is the
-  diffusion coefficient of the collective variable Q. It is calculated using the
-  Einstein relation. One can access a detailed derivation of the model elsewhere
-  \cite{liu_collective_2013}.
 
@@
 
-  %In order to fully match synthetic procedures, 
-  In order to maximally match the experimental membrane synthesis process
-  we created a cross-linking
-  algorithm that one can apply to equilibrated structures. 
-  %MRS7: I think the main purpose of crosslinking is mechanical stability.
-  The purpose of
-  cross-linking is to maintain macroscopic alignment of the crystalline domains,
-  ensuring aligned, hexagonally packed pores. For that reason, we are not
-  concerned with replicating the kinetics of the reaction, but instead emphasize
-  %MRS7: Since the initial structure isn't that well captured by experiment, then it's probably
-  % better to say that we are interested in knowing how much and in why way cross-linking modulates the structure. 
-  the consistency of the final structure with experimental structural data.
+  In order to maximally match the experimental membrane synthesis process,
+  we created a cross-linking algorithm that one can apply to equilibrated structures. 
+  The primary purpose of cross-linking is to create a mechanically robust membrane.
+  For that reason, we are not concerned with replicating the kinetics of the reaction, 
+  but instead emphasize understanding how much and in what way cross-linking modulates
+  the system's structure.
 
@@
   of the supporting info for more details on sensitivity to initial layer spacing). 
-  The pore-to-pore spacing was considered equilibrated, as defined in section~\ref{method:equil_time},
-  % BJC5: this achemso format does not have section numbers so I can't reference sections
-  % within this document.
-  in all systems after 400 ns of simulation. Figure~\ref{fig:p2p} shows the equilibrated
-  pore-to-pore distances for all systems tested.
+  We considered the pore-to-pore spacing to be equilibrated as defined in section~\ref{method:equil_time}.
+  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested.
 
@@
   %MRS7: tenses
-  %will group the systems studied here into
-  the ordered and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
+  group the systems studied here into the ordered and disordered basins. Any system where 
+  $\mathit{d}=3.7$ \AA~will be included in the
   ordered basin and any system where $\mathit{d}=5.0$ \AA~will be included in the disordered basin.
@@
   % BJC5: I think something like this has to go somewhere.
-  The diffraction patterns show some noise, especially along the axis where $q_r$=0. This
-  noise can be suppressed by sampling more uncorrelated equilibrium configurations (See 
-  section S\ref{S-section:xrd_noise}). Unfortunately, our simulations are not long enough
-  to sample enough 
-  truly
- independent configurations. 
+  The diffraction patterns show some noise, especially along the axis where $q_r$=0. There are
+  two main reasons for this noise. First is that we angle averaged the 3D structure factor 
+  (see section~\ref{method:xrd}) which inherently gives less data as q approaches 0. Second, 
+  our simulations are not long enough to sample enough truly independent configurations within
+  their respective metastable basins. By sampling more uncorrelated equilibrium configurations,
+  we can suppress some of the noise (See section S\ref{S-section:xrd_noise}).
  %MRS7: two things going on - they are not smooth because of lack of sampling WITHIN the metastable basin (somewhere in there mention angle averaging leads to less data at q=0 than anywhere else, but this is separate from being truly independent, which would mean totally converged in the equilibrium ensemble (i.e.
-reaching a single equilibrium ensemble in the >miliseconds timescale)  Increasing the number of trajectory frames
-  used to simulate the structure factor within a given interval of time does not offer 
-  any improvement.
+reaching a single equilibrium ensemble in the >miliseconds timescale)
+
+%  Increasing the number of trajectory frames used to simulate the structure factor within
+%  a given interval of time does not offer any improvement.
 %MRS7: not sure what you mean above. Increasing the frequency of frames used? 
+%BJC6: yes, since the frames are just more snapshots of non-independent configurations. I think this is already implied above.
+
   %BJC5: put figure letters in upper left hand corner of each pattern.
@@
   There are clear differences between simulated and experimental results that must be addressed
-  and justified. We will explore 
-  the 
-  %MRS7: possible or likely origin
-  origin of each experimental reflection and form structural
-  hypotheses related to their appearance in our simulated patterns. Specifically, we want answer:  
+  and justified. We will explore the possible origin of each experimental reflection and form 
+  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
+  want answer:  
   \begin{enumerate}
@@
   is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
-  The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3). R-double is still
-  not present. We will use 
-  %MRS7: be more specific when you say ``this configuration'' Just the simulation at 280K? The system is a set of configuraitons. 
-this configuration to more thoroughly explore the origin of R-spots.
+  The relative intensity of R-spots is slightly higher than in experiment (1.5 vs. 1.3). R-double 
+  is still not present. We will use the system simulated at 280K to more thoroughly explore the 
+  origin of R-spots.
 
@@
 
-%MRS7: maybe ``evidence strongly suggests that?''  
-  The R-spots signal is not a result of alkane chain tilt. Previous literature
+  Evidence strongly suggests that the R-spots signal is not a result of alkane chain tilt. Previous literature
   has attributed the spots in this particular WAXS pattern as the product of tilted alkane
@@
 	\centering
+	% remove first picture for now
 	\begin{subfigure}{0.45\linewidth}
@@
 %MRS7: what is the purpose of this paragraph?  I think most people would know why a lower T simulation would be more ordered (though the degree is not known).
-  There are a couple reasons why we see stronger ordered chain packing at 280 K compared to
+  There are two reasons why we see stronger ordered chain packing at 280 K compared to
   experimental conditions of 300 K.
@@
 
-%MRS7: discrepancies between experimental and simulated R-\pi?  
-  \subsubsection{Discrepancies between R-$\pi$}\label{section:rpi}
+  \subsubsection{Discrepancies between experimental and simulated R-$\pi$}\label{section:rpi}
 
@@
   appropriately model the aromatic $\pi-\pi$ interactions which would cause the monomers to 
-  stack closer together. Ordered basin systems are likely the best choice for transport studies.
+  stack closer together. Additionally, it is possible that the tails prevent close stacking of
+  monomer head groups and we do not achieve the timescales necessary for them to rearrange into
+  a necessarily more tightly packed configuration. Ordered basin systems are likely the best 
+  choice for transport studies.
 
@@
 %tail entropy, and for some reason ours is frozen in a configuration that is a bit too far apart. I see you talk about this later, but might need to be brought up again.
+%BJC6: tried to work that in a bit. But as you say, there is more about this point later. I could reference it here.
 
@@
   not extract a reliable correlation length from the disordered parallel displaced configuration
-  since the peak heights do not decay significantly. 
-%MRS7: perhaps ``do not show clear patters than can easily be fit to exponential decay?''
+  since the peaks do not show clear patterns than can easily be fit to exponential decay.
   %The amount of noise in the correlation function and the lack of an initial peak suggests that 
@@
 
-%MRS7: is this still true with water hydrogen information? do you need to clarify dry?
-  There is no way to produce R-double without a more complex initial configuration. We 
-  calculated the structure factor of simple systems 
-%MRS7: a little more detail, e.g. simple idealized systems with points representing monomer head groups 
-that mimic the parallel''.  Also, is ``neither'' correct? Did you do a few variants?
-  displaced and sandwiched configurations. Neither give rise to R-double. 
-  (See section S~\ref{S-section:simplified_assemblies}). The appearance of R-double implies a
-  vertical modulation in electron density every 7.4 \AA. It is possible that this modulation 
-  occurs in either the head or the tails. It is also possible that R-double does not appear in
-  a completely dry system. We will address this point in section~\ref{section:water}. There is
-  a not a unique solution to this problem, however we can speculate based on what makes the most
-  physical sense.
-%MRS7: above: vague.  Define ``this problem''. Move ``speculate'' idea to next paragraph, since that describes the speculation?  
-  We can produce R-double if our initial configuration contains alternating parallel and
-  antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
-  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). It is difficult to physically
-  justify this system. Systems built this way are only stable if position restraints are placed
-  on all head group heavy atoms. Carboxylate groups quickly revert to the parallel position as 
-  restraints are released. There is an appreciable energy barrier that prevents rotation
-  of carboxylate groups attached to phenyl rings since the group extends the system's 
-  $\pi$ conjugation (citation) (See Figure S\ref{S-fig:carboxylate_dihedral_rb}).
-  %BJC5: add citation for extended pi conjugation
-  There are instances where carboxylate groups in other systems rotate out of plane. Bushey et
-  al. showed that bulky carbonyl-containing substituents of stacked arene molecules tended to
-  tilt 45$\degree$ in order to relieve steric strain, thus allowing $\pi$-$\pi$ stacking between 
-  molecules, and to hydrogen bond with neighboring molecules. Lorenzo and Gra\~{n}a found 3
-  stable dimers of gallic acid (from which the monomer, Na-GA3C11 is derived) with adenine. In
-  all cases, the carboxylate group remained planar, even with evidence of hydrogen bonding
-  between the carboxyl group and nitrogen atoms of adenine. The monomers which we are studying
-  have no opportunities to hydrogen bond and are confined so that any rotation about the phenyl--
-  carboxylate bond would be sterically hindered.
-
-  We can also produce R-double if layers are not uniformly spaced. Rather, monomers might form 
-  pairs that stack less than 3.7~\AA~apart, and whose center of masses are spaced 7.4 \AA~ 
-  from the next pair of monomers (Figure ~\ref{fig:staggered_rzplot_norestraints}). To our 
-  knowledge, there have been no studies that specifically address the possibility of a
-  configuration like this. Our forcefield causes our system to tend towards uniformly spaced
-  layers. 
-  %As expected
-  Simulations of 
-  %this type of system 
-  unevenly spaced systems are only stable if position restraints
-  are applied to heavy atoms of the phenyl rings.
-
-  Our final hypothesized configuration which produces R-double focuses on the orientation of the
-  tails. In this configuration, monomers are rotated so that the vector created by the  
+%  There is no way to produce R-double without a more complex initial configuration. We 
+%  calculated the structure factor of simple idealize systems with points representing monomer
+%  head groups that mimic 
+%%BJC6: reference atlas of optical transforms. Get rid of idealized systems in supplemental
+%  displaced and sandwiched configurations. Neither give rise to R-double. 
+%  (See section S~\ref{S-section:simplified_assemblies}). The appearance of R-double implies a
+%  vertical modulation in electron density every 7.4 \AA. It is possible that this modulation 
+%  occurs in either the head or the tails. It is also possible that R-double does not appear in
+%  a completely dry system. We will address this point in section~\ref{section:water}.
+
+  The appearance of R-double implies a vertical modulation in electron density every 7.4 \AA.
+  We are not able to achieve such modulation using our simple initial configurations. Although
+  the position of monomers in parallel displaced configurations alternate every other layer, 
+  we know that such a helical configuration will not produce R-double, but only off-axis 
+  reflections at the same $q_z$ value ~\cite{harburn_atlas_1975}. There is not a unique solution
+  that describes the origin of R-double. Extracting the exact relationship between a diffraction
+  pattern and its real space configuration is well-known as the phase problem~\cite{taylor_phase_2003}.    
+  We have proposed configurations that result in the appearance of R-double below, and we can 
+  speculate which is makes the most physical sense. We explore both dry and wet configurations.
+
+% BJC6: removed to cut down on amount of material. This one is the biggest stretch in my opinion.
+%  We can produce R-double if our initial configuration contains alternating parallel and
+%  antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
+%  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). It is difficult to physically
+%  justify this system. Systems built this way are only stable if position restraints are placed
+%  on all head group heavy atoms. Carboxylate groups quickly revert to the parallel position as 
+%  restraints are released. There is an appreciable energy barrier that prevents rotation
+%  of carboxylate groups attached to phenyl rings since the group extends the system's 
+%  $\pi$ conjugation (citation) (See Figure S\ref{S-fig:carboxylate_dihedral_rb}).
+%  
+%  %BJC5: add citation for extended pi conjugation
+%  There are instances where carboxylate groups in other systems rotate out of plane. Bushey et
+%  al. showed that bulky carbonyl-containing substituents of stacked arene molecules tended to
+%  tilt 45$\degree$ in order to relieve steric strain, thus allowing $\pi$-$\pi$ stacking between 
+%  molecules, and to hydrogen bond with neighboring molecules. Lorenzo and Gra\~{n}a found 3
+%  stable dimers of gallic acid (from which the monomer, Na-GA3C11 is derived) with adenine. In
+%  all cases, the carboxylate group remained planar, even with evidence of hydrogen bonding
+%  between the carboxyl group and nitrogen atoms of adenine. The monomers which we are studying
+%  have no opportunities to hydrogen bond and are confined so that any rotation about the phenyl--
+%  carboxylate bond would be sterically hindered.
+
+  We can produce R-double if we rotate monomers with respect to vertically adjacent monomers.
+%  Our final hypothesized dry configuration which produces R-double focuses on the orientation of the tails. 
+  In this configuration, monomers are rotated so that the vector created by the  
   bond extending from the carboxylate carbon to the phenyl ring is oriented $\pm 15 \degree$
@@
   pack. This configuration is stable short-term while unrestrained however R-double quickly 
-  fades after a few nanoseconds of simulation. Still, this may be the most reasonable
-  way for R-double to appear in a dry system. The long-term stability of a configuration
-  similar to this may be feasible if monomers stay stacked 3.7 \AA~apart.
+  fades after a few nanoseconds of simulation. 
+  %Still, this may be the most reasonable way for R-double to appear in a dry system. 
+  The long-term stability of a configuration similar to this may be feasible if monomers stay
+  stacked 3.7 \AA~apart.
+
+  We can also produce R-double if layers are not uniformly spaced. Rather, monomers might form 
+  pairs that stack less than 3.7~\AA~apart, and whose center of masses are spaced 7.4 \AA~ 
+  from the next pair of monomers (Figure ~\ref{fig:staggered_rzplot_norestraints}). To our 
+  knowledge, there have been no studies that specifically address the possibility of a
+  configuration like this. Our forcefield causes our system to tend towards uniformly spaced
+  layers. Simulations of unevenly spaced systems are only stable if position restraints
+  are applied to heavy atoms of the phenyl rings.
+
+  Adding water to the system facilitates the appearance of R-double. We added water to the 
+  parallel displaced and sandwiched configurations in the ordered basin and equilibrated them
+  according to the wet equilibration procedure. There is no experimental measurement of 
+  water concentration in these membranes so we tested a range of water concentrations from
+  1\% to 5\%. R-double appears transiently in the simulated XRD pattern of the parallel 
+  displaced configuration with 1 wt\% water (Figure \ref{fig:solvated_pore_rzplot_norestraints}). It is
+  not initially present, but appears after 200 ns of simulation time. After 450 ns, it 
+  disappears again. Simulated XRD patterns of all other solvated systems tested are shown 
+  in Figure S~\ref{S-fig:solvation}.
 
@@
   \centering
-  %BJC4: I could cut out the tails in the three real space configurations
-  %BJC4: I can remove some of the colorbars and state that they all follow the same color bar. 
-  \begin{subfigure}{0.3\linewidth}
-  	\centering
-  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
-	\label{fig:rotated_carboxylate}
-  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%  	\centering
+%  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
+%	\label{fig:rotated_carboxylate}
+%  \end{subfigure}
   \begin{subfigure}{0.3\linewidth}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
-  	\label{fig:rotated_carboxylate_rzplot_restrained}
-  \end{subfigure}
+  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.png}
+  	\label{fig:solvated_pore}
+  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%  	\centering
+%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
+%  	\label{fig:rotated_carboxylate_rzplot_restrained}
+%  \end{subfigure}
   \begin{subfigure}{0.3\linewidth}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
-  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
-  	%BJC4: needs to run longer
-  \end{subfigure}
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
+  	\label{fig:solvated_pore_rzplot_restrained}
+  \end{subfigure}
+%  \begin{subfigure}{0.3\linewidth}
+%  	\centering
+%  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
+%  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
+%  	%BJC4: needs to run longer
+%  \end{subfigure}
   \begin{subfigure}{0.3\linewidth}
@@
   \end{subfigure}
-  \caption{R-double is present in all three inital configurations tested while the heavy atoms
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{solvated_offset_rzplot_1.png}
+  	\caption{}\label{fig:solvated_pore_rzplot_norestraints}
+  \end{subfigure}
+  \caption{R-double is present in all three initial configurations tested while the heavy atoms
   in the headgroup are held in place with position restraints. R-double fades once 
@@
 
-  \subsection{Slow dynamics}
-
-  %BJC5: this section may fit better after the next one?
-  %MRS7: yes, put it after water structuring.
-  We observe unusually slow dynamics in our system relative to other liquid crysal
-  %MRS7: are columnar liquid crystals the right comparison? Are these stickier? One could imagine that 
-  % energetic considerations in the LLCs smush them tighter together, which makes it harder for them to reorient. 
-  % in which case ours aren't atypical, but just not simulated long enough. 
-  systems. Typical diffusion constants for columnar liquid crystals have been reported
-  to be on the order of $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
-  constants of monomers in each of the systems we studied (See Table S-\ref{S-table:msd}) 
-  and learned that they are all on the order of $10^{-14}~m^2/s$.
-  Our systems may be frozen in a glassy state. It is also possible that we are simply 
-  observing characteristics of the experimental system. There has been no experimental work
-  done to study diffusion of Na-GA3C11 monomers in the Col\textsubscript{h}
-  system and no measurement of the glass transition temperature. Such a low
-  diffusion constant is not unheard of. A more recent study reported a diffusion
-  constant of $1.2\times10^{-14}~m^2/s$ for a different liquid crystal that
-  formed a hexagonal columnar phase \cite{dvinskikh_molecular_2002}.
-
-%MRS6: I don't know that the equilibration procedure induces it; I doubt a metastable state would have slower kinetics than the real state. It might be the force field is too stable. 
-%  It is possible that our equilibration procedure may induce glassy phase
-%  configurations. We have already shown that our system has some dependence on
-%  initial configuration. It is conceivable that after a fast initial relaxation,
-%  the system gets locked into a structure close to its initial configuration.
-%  The glassy state of these systems may be the reason we observe such high
-%  correlation lengths in the ordered pore basin systems. Unfortunately, we are
-%  unable to resolve the exact atomistic structure using existing experimental
-%  techniques, so we are left to find out which initial configuration results in a
-%  model with the closest match to experimental data.
-
-  Consequently, there is not enough movement on the timescales we simulated for the system to 
-  consistently reach a structure equivalent to experiment. In all cases our monomers
-  equilibrate to a stacking distance that is too large compared to experiment. 
-  While this may be in large part due to the forcefield's inability to model aromatic
-  interactions, it is also possible that the monomer tails do have enough time to pack 
-  as tightly as they could. More densely packed tails could allow the monomers to stack
-  closer together.
-
-  We quantified the movement of the tails during our simulations by calculating the 
-  autocorrelation function of the dihedral angle formed around the bond between the 
-  head groups and the ether oxygens which attach the tails to the head group 
-  (See Figure S\ref{S-fig:dihedrals}). We exclude the dihedral from the middle tail 
-  since it is fundamentally different than the two symmetric outside tails. We 
-  limited these studies to the sandwiched configuration for simplicity.
-
-  The ether dihedrals become decorrelated on a reasonable timescale when the temperature
-  is raised. At 300K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
-  not cross the x-axis until $\approx$ 105 ns meaning that tails might only fully rotate
-  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
-  function plateau's near a value of -0.2 which indicates that the tails are starting in 
-  an unfavorable configuration. We implemented distance restraints between the centers of 
-  mass of monomer head groups to preserve the hexagonal phase, then rose the temperature 
-  of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
-  decorrelation of the ether dihedrals after $\approx$ 11 ns with a plateau at 0, 
-  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
-  the resultant configuration back down to 300 K over 200 ns to see if the increased rotational
-  freedom might allow the system to relax into to a more tightly packed configuration.
-
-  Decorrelating the ether dihedrals at high temperature, followed by thermal annealing
-  does not improve packing in our model. In the ideal case, if all monomers stacked 
-  3.7 \AA~ apart, the z-dimension of our unit cell should be 7.4 nm. In the ordered basin, 
-  sandwiched system studied in this paper, the z-dimension of the unit cell equilibrated 
-  to 8.87 nm, which is roughly consistent with the stacking distance reported in 
-  Table~\ref{table:correlation_length}. After 200 ns of annealing from 500K to 300K, the 
-  z-dimension of the unit cell was 9.22 nm. We repeated the annealing procedure over the 
-  course of 400 ns and the final z-dimension of the unit cell was 9.20 nm. Much longer
-  annealing simulations may get the system to the correct density, but we do not have
-  the resources to further explore this approach. 
-  % 800K simulations are worse. Over 400 ns, the z box dimension goes to 9.8. I think this
-  % is because the initial box z-box dimension is ~10.9. In the 500K system, the initial
-  % z-box dimension is ~9.7
-
-%MRS5: let's talk about the implications of this (above); might want to move some of this into the SI.
+  R-double appears in the solvated system due to the structure of the head groups. To prove this,
+  we removed the head groups from the trajectory used to produce Figure~\ref{fig:solvation}a 
+  in order to produce that shown in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear
+  without the influence of the head groups. Water molecules must play a role in the structuring
+  of the head groups since R-double does not appear in any dry simulations.
+
+  When two vertically stacked monomer head groups hydrogen bond with a shared water 
+  molecule, the monomers are drawn closer together (as illustrated in 
+  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows 
+  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
+  with a head group below itself, it will be less likely to share a water molecule 
+  with a head group above it due to steric constraints. The monomer head group above
+  can just as easily share a water molecule with a head group above itself. In this scenario,
+  the centers of each group are 2 times the $\pi$-stacking distance apart which would
+  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
+  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
+  Peaks in the distributions represent the scenario where a monomer head group shares a 
+  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
+  we calculated the discrete fourier transform of the distributions which we used as a rough 
+  indicator of whether the head group arrangement will lead to R-double. We see the 
+  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
+  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.
+
+  The systems studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} were not truly
+  thermotropic Col\textsubscript{h} phases. Rather, they were very low water content 
+  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity.
+  This detail may be important for reproducing the results of Feng et al.
+
+%MRS7: probably want to say that this is a likely mechanism, if it can
+%occur with the given forcefield, since we had a hard time identifying any others. A more realistic forcefield
+% may make the effect stronger.
+
+  % Combine all of these figures
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
+%  \caption{Full system}\label{fig:rdouble_offset}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
+%  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
+%  \end{subfigure}
+%  \caption{The structure of the head groups is responsible for the appearance of
+%  R-double in (a). Removing head groups from the trajectory results in a simulated 
+%  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
+%  \end{figure}
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
+%  % to the floating head groups)
+%  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
+%  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
+%  drawn closer together. Head groups with blue bonds were stacked above those 
+%  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
+%  \end{figure}
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{pore_hbonds.png}
+%  \caption{}\label{fig:pore_hbonds}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
+%  \caption{}\label{fig:pore_hbonds_ft}
+%  \end{subfigure}
+%  %MRS7: add a bit more explanation - no description of discrete FT.
+%  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
+%  shared hydrogen bonded water molecule between a monomer head group and that stacked
+%  vertically above it. (b) }\label{fig:hbond_quantification}
+%  \end{figure}
 
   \begin{figure}[!htb]
-  \centering
   \begin{subfigure}{0.45\textwidth}
   \centering
-  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.png}
-  	\caption{300K}\label{fig:dihedrals_300K}
-  \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
-  	\centering
-  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.png}
-  	\caption{300K}\label{fig:dihedrals_500K}
-  \end{subfigure}
-  \caption{}\label{fig:dihedrals}
+  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
+  \caption{Full system}\label{fig:rdouble_offset}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
+  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
+  \end{subfigure}
+  \caption{}\label{fig:rdouble_origin}
+%  \caption{The structure of the head groups is responsible for the appearance of
+%  R-double in (a). Removing head groups from the trajectory results in a simulated 
+%  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
+  % to the floating head groups)
+  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
+  \caption{}\label{fig:hbond_visualization}
+%  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
+%  drawn closer together. Head groups with blue bonds were stacked above those 
+%  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{pore_hbonds.png}
+  \caption{}\label{fig:pore_hbonds}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
+  \caption{}\label{fig:pore_hbonds_ft}
+  \end{subfigure}
+  \caption{}\label{fig:hbond_quantification}
+  %MRS7: add a bit more explanation - no description of discrete FT.
+%  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
+%  shared hydrogen bonded water molecule between a monomer head group and that stacked
+%  vertically above it. (b) }\label{fig:hbond_quantification}
+  \caption{}\label{fig:figure}
   \end{figure}
@@
   \subsection{Chemical composition of pore columns}
-  %MRS7: is ``structure'' also a good word to put here? 
-  We are most interested in the composition of the pores since we would like to study
+
+  We are most interested in the structure and composition of the pores since we would like to study
   transport mechanisms within them. We have shown that the tails possess a certain degree of order
@@
 
+  %BJC6: lead with this vvv
   In general, the composition of each region, particulary the pore region, is 
@@
   \centering
-  \begin{subfigure}{0.5\textwidth}
+  \begin{subfigure}{0.32\textwidth}
         \includegraphics[width=1\linewidth]{sodium_density.png}
@@
   \end{subfigure}
-  \begin{subfigure}{0.5\textwidth}
+  \begin{subfigure}{0.32\textwidth}
         \includegraphics[width=1\linewidth]{head_group_density.png}
@@
   \end{subfigure}
-  \begin{subfigure}{0.5\textwidth}
+  \begin{subfigure}{0.32\textwidth}
         \includegraphics[width=1\linewidth]{tails_density.png}
@@
 
-  \subsection{The Effect of Water on Structure}\label{section:water}
-
-  %MRS7: generally good data, we should talk about how to tighten it up. For example, thesis shouldn't be 
-  % a history of what we did. 
-  We explored the effect of water on pore structure, addressing question
-  (\ref{point:water}), by preparing parallel displaced and sandwiched
-  configurations according to the wet equilibration procedure. We limit
-  the discussion to the ordered pore basin since it produces the most experimentally
-  consistent equilibrated configurations. There is no experimental measurement
-  of trace water concentration in these membranes so we tested a range of water
-  concentrations from 1\% to 5\%. Figure~\ref{fig:solvation} shows the simulated
-  diffraction patterns resulting from each configuration.
-
-  % formatting taken from : https://tex.stackexchange.com/questions/239715/add-titles-for-rows-and-columns-in-a-subfloat
-  \newlength{\tempdima}
-  \newcommand{\rowname}[1]% #1 = text
-  {\rotatebox{90}{\makebox[\tempdima][c]{\textbf{#1}}}}
-
-  \renewcommand{\thesubfigure}{\alph{subfigure}}
-  \newcommand{\mycaption}[1]% #1 = caption
-  {\refstepcounter{subfigure}\textbf{(\thesubfigure) }{\ignorespaces #1}}
-
-  \begin{figure}[!htb]
-  \begin{subfigure}{0.915\textwidth}
-  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
-  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
-  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
-  	\rowname{Parallel Displaced}&
-  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
-  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
-  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_5.png}\\[-1ex]
-  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
-  	\rowname{Sandwiched}&
-  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_1.png}&
-  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
-  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_5.png}\\[-1ex]
-  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
-  	\end{tabular}
-  \end{subfigure}
-  \begin{subfigure}{0.075\textwidth}
-  	\includegraphics[width=\textwidth]{colorbar_jet.png}
-  \end{subfigure}
-	\caption{Adding 1 wt \% water to the ordered basin dry systems causes an increase in the intensity
-	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
-	of water increase discrepancies with experiment %MRS7:by increasing disorder?}%
-  \label{fig:solvation}
-
-  \end{figure}
-
-  The addition of water %allows 
-  results in R-double to transiently appear. When we add 1 wt\% water to the 
-  parallel displaced configuration, R-double becomes visible (Figure~\ref{fig:rdouble_offset}). 
-  When 2.5 wt\% water is added, R-double disappears, but the helical reflections characteristic
-  of the parallel displaced configuration become more diffuse, which is a closer match to 
-  experiment. If water is truly responsible for R-double, then there is likely
-  between 1 and 2.5 wt\% water absorbed into the membrane. 
-%MRS7: this is limited by the force field and strength of hydrogen bonding. ``is likely'' is strong.
-This does not exclude 
-  possible contributions from the motifs discussed in section~\ref{section:rdouble}. Water
-  may facilitate the stability of such motifs. 
-%  However, given the long-term stability of this configuration, it is most likely that small
-%  amounts of water are responsible for the existence of R-double.
-
-%MRS7: should this be first in the section as motivation.
-  The systems studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} were not truly
-  thermotropic Col\textsubscript{h} phases. Rather, they were very low water content 
-  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity.
-  This detail may be important for reproducing the results of Feng et al.
-
-  R-double appears due to the structure of the head groups. We removed the head groups from the
-  trajectory used to produce Figure~\ref{fig:solvation}a in order to produce that shown
-  in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear without the influence of the
-  head groups. Water molecules must play a role in the structuring of the head groups since 
-  R-double does not appear in any dry simulations.
-
-%  Water causes the monomer head groups to restructure.   
-%  We confirmed that the reflection is 
-%  not caused by the water itself. We removed all water molecules from the trajectory and 
-%  showed that R-double is still present in the simulated diffraction pattern 
-%  (Figure~\ref{fig:rdouble_nowater}). We also confirmed that the tails are not responsible for
-%  R-double. R-double is not present when we remove all atoms except carbon atoms that make
-%  up the tails (Figure~\ref{fig:rdouble_tails}). It is clear that interactions between water
-%  and head groups causes them to restructure in a way that leads to R-double.
-
-  % BJC5: This figure may belong in supplemental
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
-  \caption{Full system}\label{fig:rdouble_offset}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
-  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
-  \end{subfigure}
-%  \begin{subfigure}{0.32\textwidth}
-%  \includegraphics[width=\textwidth]{rdouble_tails_only_rzplot.png}
-%  \caption{Tails only}\label{fig:rdouble_tails}
-%  \end{subfigure}
-  \caption{The structure of the head groups is responsible for the appearance of
-  R-double in (a). Removing head groups from the trajectory results in a simulated 
-  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
-  \end{figure}
-
-  When two vertically stacked monomer head groups hydrogen bond with a shared water 
-  molecule, the monomers are drawn closer together (as illustrated in 
-  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows 
-  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
-  with a head group below itself, it will be less likely to share a water molecule 
-  with a head group above it due to steric constraints. The monomer head group above
-  can just as easily share a water molecule with a head group above itself. In this scenario,
-  the centers of each group are 2 times the $\pi$-stacking distance apart which would
-  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
-  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
-  Peaks in the distributions represent the scenario where a monomer head group shares a 
-  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
-  we calculated the discrete fourier transform of the distributions which we used as a rough 
-  indicator of whether the head group arrangement will lead to R-double. We see the 
-  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
-  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.
-
-%MRS7: probably want to say that this is a likely mechanism, if it can
-%occur with the given forcefield, since we had a hard time identifying any others. A more realistic forcefield
-% may make the effect stronger.
-
-  \begin{figure}[!htb]
-  \centering
-  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
-  % to the floating head groups)
-  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
-  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
-  drawn closer together. Head groups with blue bonds were stacked above those 
-  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
-  \end{figure}
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{pore_hbonds.png}
-  \caption{}\label{fig:pore_hbonds}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
-  \caption{}\label{fig:pore_hbonds_ft}
-  \end{subfigure}
-  %MRS7: add a bit more explanation - no description of discrete FT.
-  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
-  shared hydrogen bonded water molecule between a monomer head group and that stacked
-  vertically above it. (b) }\label{fig:hbond_quantification}
-  \end{figure}
+%  \subsection{The Effect of Water on Structure}\label{section:water}
+%
+%  %MRS7: generally good data, we should talk about how to tighten it up. For example, thesis shouldn't be 
+%  % a history of what we did. 
+%  We explored the effect of water on pore structure, addressing question
+%  (\ref{point:water}), by preparing parallel displaced and sandwiched
+%  configurations according to the wet equilibration procedure. We limit
+%  the discussion to the ordered pore basin since it produces the most experimentally
+%  consistent equilibrated configurations. There is no experimental measurement
+%  of trace water concentration in these membranes so we tested a range of water
+%  concentrations from 1\% to 5\%. Figure~\ref{fig:solvation} shows the simulated
+%  diffraction patterns resulting from each configuration.
+%  
+%  % formatting taken from : https://tex.stackexchange.com/questions/239715/add-titles-for-rows-and-columns-in-a-subfloat
+%  \newlength{\tempdima}
+%  \newcommand{\rowname}[1]% #1 = text
+%  {\rotatebox{90}{\makebox[\tempdima][c]{\textbf{#1}}}}
+%  
+%  \renewcommand{\thesubfigure}{\alph{subfigure}}
+%  \newcommand{\mycaption}[1]% #1 = caption
+%  {\refstepcounter{subfigure}\textbf{(\thesubfigure) }{\ignorespaces #1}}
+%  
+%  \begin{figure}[!htb]
+%  \begin{subfigure}{0.915\textwidth}
+%  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
+%  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
+%  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
+%  	\rowname{Parallel Displaced}&
+%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
+%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
+%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_5.png}\\[-1ex]
+%  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
+%  	\rowname{Sandwiched}&
+%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_1.png}&
+%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
+%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_5.png}\\[-1ex]
+%  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
+%  	\end{tabular}
+%  \end{subfigure}
+%  \begin{subfigure}{0.075\textwidth}
+%  	\includegraphics[width=\textwidth]{colorbar_jet.png}
+%  \end{subfigure}
+%	\caption{Adding 1 wt \% water to the ordered basin dry systems causes an increase in the intensity
+%	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
+%	of water increase discrepancies with experiment} %MRS7:by increasing disorder?
+%  \label{fig:solvation}
+%
+%  \end{figure}
+% 
+%  The addition of water %allows 
+%  results in R-double to transiently appear. When we add 1 wt\% water to the 
+%  parallel displaced configuration, R-double becomes visible (Figure~\ref{fig:rdouble_offset}). 
+%  When 2.5 wt\% water is added, R-double disappears, but the helical reflections characteristic
+%  of the parallel displaced configuration become more diffuse, which is a closer match to 
+%  experiment. If water is truly responsible for R-double, then there is likely
+%  between 1 and 2.5 wt\% water absorbed into the membrane. 
+%%MRS7: this is limited by the force field and strength of hydrogen bonding. ``is likely'' is strong.
+%This does not exclude 
+%  possible contributions from the motifs discussed in section~\ref{section:rdouble}. Water
+%  may facilitate the stability of such motifs. 
+%%  However, given the long-term stability of this configuration, it is most likely that small
+%%  amounts of water are responsible for the existence of R-double.  
+%  
+%%MRS7: should this be first in the section as motivation.
+%  The systems studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} were not truly
+%  thermotropic Col\textsubscript{h} phases. Rather, they were very low water content 
+%  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity.
+%  This detail may be important for reproducing the results of Feng et al.
+%  
+%  R-double appears due to the structure of the head groups. We removed the head groups from the
+%  trajectory used to produce Figure~\ref{fig:solvation}a in order to produce that shown
+%  in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear without the influence of the
+%  head groups. Water molecules must play a role in the structuring of the head groups since 
+%  R-double does not appear in any dry simulations.
+%  
+%%  Water causes the monomer head groups to restructure.   
+%%  We confirmed that the reflection is 
+%%  not caused by the water itself. We removed all water molecules from the trajectory and 
+%%  showed that R-double is still present in the simulated diffraction pattern 
+%%  (Figure~\ref{fig:rdouble_nowater}). We also confirmed that the tails are not responsible for
+%%  R-double. R-double is not present when we remove all atoms except carbon atoms that make
+%%  up the tails (Figure~\ref{fig:rdouble_tails}). It is clear that interactions between water
+%%  and head groups causes them to restructure in a way that leads to R-double.
+%  
+%  
+%  % BJC5: This figure may belong in supplemental
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
+%  \caption{Full system}\label{fig:rdouble_offset}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
+%  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
+%  \end{subfigure}
+%%  \begin{subfigure}{0.32\textwidth}
+%%  \includegraphics[width=\textwidth]{rdouble_tails_only_rzplot.png}
+%%  \caption{Tails only}\label{fig:rdouble_tails}
+%%  \end{subfigure}
+%  \caption{The structure of the head groups is responsible for the appearance of
+%  R-double in (a). Removing head groups from the trajectory results in a simulated 
+%  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
+%  \end{figure}
+%
+%  When two vertically stacked monomer head groups hydrogen bond with a shared water 
+%  molecule, the monomers are drawn closer together (as illustrated in 
+%  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows 
+%  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
+%  with a head group below itself, it will be less likely to share a water molecule 
+%  with a head group above it due to steric constraints. The monomer head group above
+%  can just as easily share a water molecule with a head group above itself. In this scenario,
+%  the centers of each group are 2 times the $\pi$-stacking distance apart which would
+%  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
+%  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
+%  Peaks in the distributions represent the scenario where a monomer head group shares a 
+%  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
+%  we calculated the discrete fourier transform of the distributions which we used as a rough 
+%  indicator of whether the head group arrangement will lead to R-double. We see the 
+%  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
+%  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.
+%
+%%MRS7: probably want to say that this is a likely mechanism, if it can
+%%occur with the given forcefield, since we had a hard time identifying any others. A more realistic forcefield
+%% may make the effect stronger.
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
+%  % to the floating head groups)
+%  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
+%  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
+%  drawn closer together. Head groups with blue bonds were stacked above those 
+%  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
+%  \end{figure}
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{pore_hbonds.png}
+%  \caption{}\label{fig:pore_hbonds}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
+%  \caption{}\label{fig:pore_hbonds_ft}
+%  \end{subfigure}
+%  %MRS7: add a bit more explanation - no description of discrete FT.
+%  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
+%  shared hydrogen bonded water molecule between a monomer head group and that stacked
+%  vertically above it. (b) }\label{fig:hbond_quantification}
+%  \end{figure}
 
@@
 
+  \subsection{Slow dynamics}
+
+  We observe unusually slow dynamics in our system relative to other liquid crysal
+  %MRS7: are columnar liquid crystals the right comparison? Are these stickier? One could imagine that 
+  % energetic considerations in the LLCs smush them tighter together, which makes it harder for them to reorient. 
+  % in which case ours aren't atypical, but just not simulated long enough. 
+  systems. Typical diffusion constants for columnar liquid crystals have been reported
+  to be on the order of $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
+  constants of monomers in each of the systems we studied (See Table S-\ref{S-table:msd}) 
+  and learned that they are all on the order of $10^{-14}~m^2/s$.
+  Our systems may be frozen in a glassy state. It is also possible that we are simply 
+  observing characteristics of the experimental system. There has been no experimental work
+  done to study diffusion of Na-GA3C11 monomers in the Col\textsubscript{h}
+  system and no measurement of the glass transition temperature. Such a low
+  diffusion constant is not unheard of. A more recent study reported a diffusion
+  constant of $1.2\times10^{-14}~m^2/s$ for a different liquid crystal that
+  formed a hexagonal columnar phase \cite{dvinskikh_molecular_2002}.
+
+%MRS6: I don't know that the equilibration procedure induces it; I doubt a metastable state would have slower kinetics than the real state. It might be the force field is too stable. 
+%  It is possible that our equilibration procedure may induce glassy phase
+%  configurations. We have already shown that our system has some dependence on
+%  initial configuration. It is conceivable that after a fast initial relaxation,
+%  the system gets locked into a structure close to its initial configuration.
+%  The glassy state of these systems may be the reason we observe such high
+%  correlation lengths in the ordered pore basin systems. Unfortunately, we are
+%  unable to resolve the exact atomistic structure using existing experimental
+%  techniques, so we are left to find out which initial configuration results in a
+%  model with the closest match to experimental data.
+
+  Consequently, there is not enough movement on the timescales we simulated for the system to 
+  consistently reach a structure equivalent to experiment. In all cases our monomers
+  equilibrate to a stacking distance that is too large compared to experiment. 
+  While this may be in large part due to the forcefield's inability to model aromatic
+  interactions, it is also possible that the monomer tails do have enough time to pack 
+  as tightly as they could. More densely packed tails could allow the monomers to stack
+  closer together.
+
+  We quantified the movement of the tails during our simulations by calculating the 
+  autocorrelation function of the dihedral angle formed around the bond between the 
+  head groups and the ether oxygens which attach the tails to the head group 
+  (See Figure S\ref{S-fig:dihedrals}). We exclude the dihedral from the middle tail 
+  since it is fundamentally different than the two symmetric outside tails. We 
+  limited these studies to the sandwiched configuration for simplicity.
+
+  The ether dihedrals become decorrelated on a reasonable timescale when the temperature
+  is raised. At 300K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
+  not cross the x-axis until $\approx$ 105 ns meaning that tails might only fully rotate
+  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
+  function plateau's near a value of -0.2 which indicates that the tails are starting in 
+  an unfavorable configuration. We implemented distance restraints between the centers of 
+  mass of monomer head groups to preserve the hexagonal phase, then rose the temperature 
+  of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
+  decorrelation of the ether dihedrals after $\approx$ 11 ns with a plateau at 0, 
+  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
+  the resultant configuration back down to 300 K over 200 ns to see if the increased rotational
+  freedom might allow the system to relax into to a more tightly packed configuration.
+
+  Decorrelating the ether dihedrals at high temperature, followed by thermal annealing
+  does not improve packing in our model. In the ideal case, if all monomers stacked 
+  3.7 \AA~ apart, the z-dimension of our unit cell should be 7.4 nm. In the ordered basin, 
+  sandwiched system studied in this paper, the z-dimension of the unit cell equilibrated 
+  to 8.87 nm, which is roughly consistent with the stacking distance reported in 
+  Table~\ref{table:correlation_length}. After 200 ns of annealing from 500K to 300K, the 
+  z-dimension of the unit cell was 9.22 nm. We repeated the annealing procedure over the 
+  course of 400 ns and the final z-dimension of the unit cell was 9.20 nm. Much longer
+  annealing simulations may get the system to the correct density, but we do not have
+  the resources to further explore this approach. 
+  % 800K simulations are worse. Over 400 ns, the z box dimension goes to 9.8. I think this
+  % is because the initial box z-box dimension is ~10.9. In the 500K system, the initial
+  % z-box dimension is ~9.7
+
+%MRS5: let's talk about the implications of this (above); might want to move some of this into the SI.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.png}
+  	\caption{300K}\label{fig:dihedrals_300K}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.png}
+  	\caption{300K}\label{fig:dihedrals_500K}
+  \end{subfigure}
+  \caption{}\label{fig:dihedrals}
+  \end{figure}
+
   \subsection{Model Ionic Conductivity Measurements}
@@
 we did X, it was noiser, but agreed within data (see SI).
-  We used equilibrated systems in the ordered pore basin to calculate ionic 
-  conductivity since we believe their structures are the closest match to
-  experiment. Our models give reasonable estimates of ionic conductivity when
-  compared to experiment. We compare calculated values of ionic conductivity
-  obtained using the Nernst-Einstein relation and Collective Diffusion model in
-  % names of equations capitalized?
-  Figure~\ref{fig:conductivity}. The two methods agree with each other within
-  error, although the uncertainty obtained using the Collective Diffusion model
-  is much higher. We require much longer simulations to lower the uncertainty,
-  however it is not feasible to do so with a large system. We will only use the
-  Nernst-Einstein relation in future calculations of this type.
-
-  The calculated values of ionic conductivity are higher than experiment by an
-  order of magnitude. One can justify the reason for this result by considering
-  the real system studied experimentally. The ionic conductivity measurement to
-  which we are comparing was done with a \SI{80}{\micro\metre} thick film, nearly
-  10,000 times thicker than our simulated system. The thick film is likely
-  imperfectly aligned and has defects leading to non-contiguous pores. It has
-  been shown that there is a large dependence of ionic conductivity on the
-  alignment of the pores. The ionic conductivity of an isotropically aligned film
-  is ca. 85 times lower than that of a nearly aligned film referenced
-  here~\cite{feng_scalable_2014}. We hypothesize that a thin, perfectly aligned
-  film would have a value of ionic conductivity in closer agreement with our
-  model.
-
-  \begin{figure}[!htb]
-        \centering
-        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
-        \caption{The Collective Diffusion model and the nernst-einstein relation yield
-        agreeing values of ionic conductivity for both systems simulated. Both methods
-        estimate the value of the ionic conductivity to be an order of magnitude higher 
-        than the experimental value.}
-        \label{fig:conductivity}
+
+  %BJC6: shifted to solvated system only. Moved Collective diffusion to supporting info.
+
+%  We used equilibrated systems in the ordered pore basin to calculate ionic 
+%  conductivity since we believe their structures are the closest match to
+%  experiment.
+
+  We calculated the ionic conductivity of the parallel displaced configuration in
+  the ordered basin with 1 wt \% water since we believe its structure is the 
+  closest match to experiment. Our model estimates the ionic conductivity within
+  one order of magnitude of experiment (Figure~\ref{fig:ionic_conductivity}). We
+  verified the value calculated by the Nernst-Einstein relationship using a 
+  second method called the collective diffusion model\cite{liu_collective_2013} 
+  (See section S~\ref{s-fig:conductivity}). The values calculated by the 
+  collective diffusion model agree with Nernst-Einstein  values within error, 
+  however there is a much higher uncertainty that would require much longer 
+  simulations to lower.
+
+%  We compare calculated values of ionic conductivity obtained using the 
+%  Nernst-Einstein relation and Collective Diffusion model in Figure~\ref{fig:conductivity}.
+%  The two methods agree with each other within error, although the uncertainty
+%  obtained using the Collective Diffusion model is much higher. We require much longer simulations to lower the uncertainty,
+%  however it is not feasible to do so with a large system. We will only use the
+%  Nernst-Einstein relation in future calculations of this type.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{IC_nernst.png}
+  \caption{The calculated ionic conductivity of the simulated system is approximately
+  one order of magnitude higher than experiment.}\label{fig:ionic_conductivity}
   \end{figure}
+
+  The calculate value of ionic conductivity is 5x higher than experiment because 
+  we simulated infinitely long, aligned pores.
+%  The calculated values of ionic conductivity are higher than experiment by an
+%  order of magnitude. One can justify the reason for this result by considering
+%  the real system studied experimentally. 
+  The ionic conductivity measurement to which we are comparing was done with a
+  \SI{80}{\micro\metre} thick film, nearly 10,000 times thicker than our simulated
+  system. The thick film is likely imperfectly aligned and has defects leading to
+  non-contiguous pores. It has been shown that there is a large dependence of 
+  ionic conductivity on the alignment of the pores. The ionic conductivity of an
+  isotropically aligned film is ca. 85 times lower than that of the nearly aligned
+  film to which we are comparing~\cite{feng_scalable_2014}. We hypothesize that a 
+  thin, perfectly aligned film would have a value of ionic conductivity in closer
+  agreement with our model.
 

### 2018-06-13 Ben_Manuscripts/structure_paper/Draft.tex
More draft edits and figure updates

@@
         %that although rdouble isn't there, for the more structured ones, there is a 7.4 band, even if it disappears at q=0.
+        %BJC6: 7.4 band is any parallel displaced configuration, not more structured systems.
   \end{figure}
@@
   %MRS7: huh.
+  %BJC6: yea, specifically the one for j phys chem B. I compiled with a different document type and the captions looked normal
   There are clear differences between simulated and experimental results that must be addressed
@@
 
+  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
+  configuration at 280K. Obtaining an equilibrium structure at a precise temperature is
+  a challenge that force fields often fail to overcome. Wang et al. highlighted the 
+  shortcoming of some of the most popular protein force field in predicting the temperature
+  dependence of protein structural ensembles \cite{wang_building_2017}. It is possible that   % page 12
+  our membrane system, simulated at 300K, does not fully represent the true structure at 300K.
+
   We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
@@
 %  before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.
+
+% BJC6 : added better justification to beginning of section
+%  %MRS7: couple -> ``two main''?
+%%MRS7: what is the purpose of this paragraph?  I think most people would know why a lower T simulation would be more ordered (though the degree is not known).
+%  There are two reasons why we see stronger ordered chain packing at 280 K compared to
+%  experimental conditions of 300 K.
+%  \begin{enumerate}
+%  		\item The difference between 280 K and 300 K is relatively small. Our forcefield parameters
+%  		may not correctly model the behavior of the tails at 300 K (citation?).
+%                % look for papers on protien folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
+%  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
+%  		If the head groups packed 3.7 \AA~apart, the tails would be more confined and forced
+%  		to pack between vertically adjacent monomer tails. In our case, the tail region is
+%  		less dense than experiment which gives the tails freedom to organize in a more
+%  		entropically favored disordered state. 
+%  \end{enumerate}
 
@@
 
-%MRS7: couple -> ``two main''?
-%MRS7: what is the purpose of this paragraph?  I think most people would know why a lower T simulation would be more ordered (though the degree is not known).
-  There are two reasons why we see stronger ordered chain packing at 280 K compared to
-  experimental conditions of 300 K.
-  \begin{enumerate}
-  		\item The difference between 280 K and 300 K is relatively small. Our forcefield parameters
-  		may not correctly model the behavior of the tails at 300 K (citation?).
-                % look for papers on protien folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
-  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
-  		If the head groups packed 3.7 \AA~apart, the tails would be more confined and forced
-  		to pack between vertically adjacent monomer tails. In our case, the tail region is
-  		less dense than experiment which gives the tails freedom to organize in a more
-  		entropically favored disordered state. 
-  \end{enumerate}
-
   \subsubsection{Discrepancies between experimental and simulated R-$\pi$}\label{section:rpi}
 
+  There is not a single reason for the high intensity of R-$\pi$ in our simulations.
+  We used one-dimensional pair distribution functions of the centers of masses of monomer
+  phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
+  columns and the degree to which they are correlated. These metrics helped us disect the 
+  various contributions to R-$\pi$. Figure ~\ref{fig:correlation} shows $g(z)$ for all 
+  systems tested.
+
+%  The first peak of $g(z)$ is larger in the ordered
+%  basin systems compared to those in the disordered basin. This observation is indicative
+%  of a higher degree of local ordering in the ordered basin systems which causes an
+%  increase in the intensity of R-$\pi$.
+
   %MRS7: not a strong thesis sentence.
-  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
-  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). We used this 
-  information to understand how far apart monomers stack within monomer columns and
-  the degree to which they are correlated.
+%  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
+%  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). We used this 
+%  information to understand how far apart monomers stack within monomer columns and
+%  the degree to which they are correlated.
 
@@
 
+  %We expect that when monomers stack closer together, steric clashes
+  %force head groups to orient in a more ordered fashion. If head groups in our model stayed 3.7 \AA
+  %apart, we may actually see higher values of R-$\pi$ due to enhance order.
+
 %MRS7: other hypothesis about stacking that comes from Matt's implications is that it may have to do with
@@
 
-  The correlation length between stacked monomer head groups of the ordered systems also show
-  closer agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
+  The correlation length of the parallel displaced, ordered basin system shows
+  the closest agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
   correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
   not extract a reliable correlation length from the disordered parallel displaced configuration
-  since the peaks do not show clear patterns than can easily be fit to exponential decay.
+  since the peaks do not show clear patterns that can easily be fit to exponential decay. The 
+  correlation length of both sandwiched systems is relatively low because the height of the first
+  peak of $g(z)$ is so high. The peak height indicates the degree of local ordering and influences
+  the intensity of R-$pi$. If vertically adjacent sandwiched head groups were less ordered, which
+  might be achieved with much longer simulations, then the leading peak intensity should decrease and
+  the correlation length would increase. We expect that the leading peak would only get more intense 
+  if monomers stacked 3.7 \AA apart. Conversely, parallel displaced head groups are not as confined
+  by their vertically adjacent neighbors. This z-direction translational freedom may still be 
+  feasible if monomers stack 3.7 \AA apart in a parallel displaced configuration.
+
   %The amount of noise in the correlation function and the lack of an initial peak suggests that 
   %the correlation length is less than $\mathit{d}_{equil}$.
-  In general, we see that correlation length increases as monomers stack closer together. The same
-  trend has been seen in molecular dynamics studies of polymer fluids~\cite{koshy_density_2003}.
-  We hypothesize that the correlation length of the sandwiched configuration would increase to a
-  value near experiment if monomers packed closer together.
+  %BJC6: not supported by data vv
+%  In general, we see that correlation length increases as monomers stack closer together. The same
+%  trend has been seen in molecular dynamics studies of polymer fluids~\cite{koshy_density_2003}.
+%  We hypothesize that the correlation length of the sandwiched configuration would increase to a
+%  value near experiment if monomers packed closer together.
 
@@
   %intensity of the peaks that much.  If so, this isn't a great explanation. 
-  The simulated intensity of R-$\pi$ is also more intense than experiment because our system
-  models near-perfectly straight pores with no defects. Nearly all of the intensity in 
-  R-$\pi$ of our simulated patterns is concentrated at a single point. Figure~\ref{fig:simulated_adjusted_colorbar}
-  shows the simulated pattern of the ordered sandwiched configuration with the upper boundary
-  on the colorbar adjusted to be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only
-  distinguishable reflections are those of R-$\pi$ and R-pores. In the experimental pattern 
-  (Figure~\ref{fig:experimental_adjusted_colorbar}), the intensity is more evenly spread out
-  over all of R-$\pi$. 
+  %BJC6: worked this into other paragraphs. I find this paragraph awkward and the figure unnecessary.
+%  The simulated intensity of R-$\pi$ is also more intense than experiment due to strong local
+%  ordering. Nearly all of the intensity in R-$\pi$ of our simulated patterns is concentrated 
+%  at a single point. Figure~\ref{fig:simulated_adjusted_colorbar} shows the simulated pattern
+%  of the ordered sandwiched configuration with the upper boundary on the colorbar adjusted to
+%  be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only distinguishable reflections
+%  are those of R-$\pi$ and R-pores. In the experimental pattern 
+%  (Figure~\ref{fig:experimental_adjusted_colorbar}), the intensity is more evenly spread out
+%  over all of R-$\pi$. 
   % BJC5: I'm not sure how well supported the above paragraph is by the below figure. Need to figure 
@@
 
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.4\textwidth}
-	  \includegraphics[width=\linewidth]{sandwich_rzplot_highlimit_cbar.png}
-	  \caption{}\label{fig:simulated_adjusted_colorbar}
-  \end{subfigure}
-  \begin{subfigure}{0.4\textwidth}
-	  \includegraphics[width=\linewidth]{WAXS_raw_adjusted_colorbar.png}
-	  \caption{}\label{fig:experimental_adjusted_colorbar}
-  \end{subfigure}
-  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections in 
-  simulated diffraction patterns (a). Here, the colorbar was scaled so that the max is 6x
-  higher than all other plots.}\label{fig:intense_rpi}
-  \end{figure}
+  %BJC6: not sure if this should go in supplemental
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.4\textwidth}
+%	  \includegraphics[width=\linewidth]{sandwich_rzplot_highlimit_cbar.png}
+%	  \caption{}\label{fig:simulated_adjusted_colorbar}
+%  \end{subfigure}
+%  \begin{subfigure}{0.4\textwidth}
+%	  \includegraphics[width=\linewidth]{WAXS_raw_adjusted_colorbar.png}
+%	  \caption{}\label{fig:experimental_adjusted_colorbar}
+%  \end{subfigure}
+%  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections in 
+%  the simulated diffraction patterns (a). Here, the colorbar was scaled so that the max is 6x
+%  higher than all other plots.}\label{fig:intense_rpi}
+%  \end{figure}
 
@@
   	\centering
-  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.png}
+  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.png}  %BJC6: I can simplify this more (stacked monomers on each side with a few water molecules in between.
   	\label{fig:solvated_pore}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
+  	\includegraphics[width=\textwidth]{solvated_pore_rzplot_restrained.png}
   	\label{fig:solvated_pore_rzplot_restrained}
@@
   \end{subfigure}
-  \caption{R-double is present in all three initial configurations tested while the heavy atoms
-  in the headgroup are held in place with position restraints. R-double fades once 
-  the position restriants are released.}\label{fig:rdouble}
+  \caption{(a) When monomers are non-uniformly spaced (top), R-double appears if all heavy atoms
+  of the head groups are held in place with position restraints (middle). R-double quickly fades once 
+  the position restraints are released (bottom). (b) When monomer head groups are rotated with respect
+  to vertically adjacent monomers (top), R-double is visible while the heavy atoms of the head groups
+  are held in place with position restraints (middle). Again, R-double fades once the position 
+  restraints are released. (c) When we add 1 wt\% water to the parallel displaced configuration in the
+  ordered basin (top) R-double is not initially present during the restrained portion of equilibration (middle).
+  After 200 ns of equilibration, R-double becomes visible and persists for another 200 ns (bottom).}\label{fig:rdouble}
   \end{figure}
@@
   R-double appears in the solvated system due to the structure of the head groups. To prove this,
-  we removed the head groups from the trajectory used to produce Figure~\ref{fig:solvation}a 
+  we removed the head groups from the trajectory used to produce Figure~\ref{fig:solvated_pore_rzplot_norestraints}
   in order to produce that shown in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear
@@
   R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
-  with a head group below itself, it will be less likely to share a water molecule 
-  with a head group above it due to steric constraints. The monomer head group above
-  can just as easily share a water molecule with a head group above itself. In this scenario,
-  the centers of each group are 2 times the $\pi$-stacking distance apart which would
-  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
+  with a head group above itself, it will be less likely to share a water molecule 
+  with a head group below it due to steric constraints. The monomer head group below
+  can just as easily share a water molecule with a head group below itself. In this scenario,
+  the centers of each pair are 2 times the $\pi$-stacking distance apart which would
+  lead to R-double (much like the configuration in Figure~\ref{fig:staggered_rzplot_norestraints}). There are
   a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
@@
 
-  The systems studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} were not truly
-  thermotropic Col\textsubscript{h} phases. Rather, they were very low water content 
-  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity.
-  This detail may be important for reproducing the results of Feng et al.
-
-%MRS7: probably want to say that this is a likely mechanism, if it can
-%occur with the given forcefield, since we had a hard time identifying any others. A more realistic forcefield
-% may make the effect stronger.
-
-  % Combine all of these figures
-%  \begin{figure}[!htb]
-%  \centering
+  It is likely that R-double originates from water molecules as described above and it is the 
+  only mechanism that occurred without using position restraints. The extent of the hydrogen
+  bonding network that forms is largely determined by the accuracy of the forcefield. It is 
+  possible that a more realistic forcefield would make the effect stronger or weaker. If 
+  this is truly the mechanism, it implies that the systems studied by Feng et 
+  al.\cite{feng_scalable_2014,feng_thin_2016} were not truly thermotropic Col\textsubscript{h}
+  phases. Rather, they were very low water content H\textsubscript{II} phases unintentionally
+  created due to the neat monomers' hydroscopicity. This detail may be important for reproducing
+  the results of Feng et al.
+
+  \begin{figure}[!htb]
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  % BJC6 : below is the simulated diffraction pattern of the full system. I removed it since showing both
+  % makes both patterns small. You can see the full pattern in a separate figure.
 %  \begin{subfigure}{0.45\textwidth}
 %  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}  
-%  \caption{Full system}\label{fig:rdouble_offset}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
-%  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
-%  \end{subfigure}
-%  \caption{The structure of the head groups is responsible for the appearance of
-%  R-double in (a). Removing head groups from the trajectory results in a simulated 
-%  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
-%  \end{figure}
-%  
-%  \begin{figure}[!htb]
-%  \centering
-%  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
-%  % to the floating head groups)
-%  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
-%  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
-%  drawn closer together. Head groups with blue bonds were stacked above those 
-%  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
-%  \end{figure}
-%  
-%  \begin{figure}[!htb]
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{pore_hbonds.png}
-%  \caption{}\label{fig:pore_hbonds}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
-%  \caption{}\label{fig:pore_hbonds_ft}
-%  \end{subfigure}
-%  %MRS7: add a bit more explanation - no description of discrete FT.
-%  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
-%  shared hydrogen bonded water molecule between a monomer head group and that stacked
-%  vertically above it. (b) }\label{fig:hbond_quantification}
-%  \end{figure}
-
-  \begin{figure}[!htb]
+%  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
+  \end{subfigure}
+  \caption{}\label{fig:rdouble_nophenyls}
+  \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
   \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
-  \caption{Full system}\label{fig:rdouble_offset}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
-  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
-  \end{subfigure}
-  \caption{}\label{fig:rdouble_origin}
-%  \caption{The structure of the head groups is responsible for the appearance of
-%  R-double in (a). Removing head groups from the trajectory results in a simulated 
-%  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
-  % to the floating head groups)
-  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
+  \includegraphics[width=\textwidth]{hbonds_tails.png}
   \caption{}\label{fig:hbond_visualization}
-%  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
-%  drawn closer together. Head groups with blue bonds were stacked above those 
-%  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
   \end{subfigure}
@@
   \end{subfigure}
-  \caption{}\label{fig:hbond_quantification}
-  %MRS7: add a bit more explanation - no description of discrete FT.
-%  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
-%  shared hydrogen bonded water molecule between a monomer head group and that stacked
-%  vertically above it. (b) }\label{fig:hbond_quantification}
-  \caption{}\label{fig:figure}
+  \caption{(a) The structure of the head groups is responsible for the appearance of
+  R-double. When we remove head groups from the trajectory, the simulated 
+  diffraction pattern no longer shows R-double. (b) Monomer head groups above or below
+  each other that hydrogen bond with a shared water molecule are drawn closer
+  together. Blue monomers were stacked above orange monomers in the initial configuration.
+  (c) Monomers in each column are numbered from 1--20. For simplicity, we define a layer to
+  be composed of all same-number monomers. Peaks in the distributions indicate
+  a shared hydrogen bonded water molecule between a monomer head group and one in the layer
+  vertically above it. For example, in Pore 1, monomer 7 shares a hydrogen bond with
+  a monomer in layer 8 (pictured in (b)). In this scenario, monomers are no longer evenly
+  spaced in the z-direction since they are pulled closer together by hydrogen bonds. 
+  (d) We performed discrete fourier transforms on each distribution in (c). In all cases,
+  the strongest peak represents periodicity every layer. In Pore 1, there is also periodicity
+  every other layer as indicated by the strong peak at 0.5 layers$^{-1}$. In this case, the
+  center of mass of two adjacent pairs is separated by twice the average monomer stacking 
+  distance, while the four monomers involved are unequally spaced. These conditions may
+  give rise to R-double.}\label{fig:hbonds}
   \end{figure}
@@
 
+  %BJC6: moved this paragraph up to make the section more idea-focused
+  In general, the composition of each region, particulary within our definition of 
+  the pore region, is similar between all systems. We believe we can solvate and study transport
+  in any of the systems presented here and extract similar transport mechanisms. We will 
+  need to verify that this assumption is true.
+
   We plotted the number densities of heavy atoms in the head group, carbon atoms in the tail
@@
 
-  %MRS7: this section reads a little bit as ``and then, and
-  %then''. Think how to make it more focused on core ideas to communicate. Thes is they are all about the same. Perhaps should be the beginning of the section?
-
-  %MRS7: rephrase? Partition implies more abrupt.
-  There is a partition between the hydrophobic and hydrophilic regions, however
-  it is a gradient in composition, rather than an abrupt division. The system
-  does not confine sodium ions and head groups to just within the pore region.
-  Based on size-exclusion experiments, we define the pore radius to be 0.6 nm
+  There is a gradient in pore composition transitioning radially from the hydrophilic 
+  to the hydrophobic region, rather than an abrupt division. Based on size-exclusion 
+  experiments, we define the pore radius to be 0.6 nm
   %BJC5 : Add vertical line to plots for 'pore radius'? Might be too busy.
-  ~\cite{zhou_supported_2005}. We see in all cases, that 19\% of sodium ions
-  exist outside the pore region (except sandwiched, ordered basin, where 16\%
-  are outside the pore). Additionally, we see that in all cases, about 3\% of the
-  plotted tail density is located within the pore region (except ordered sandwiched,
-  where 1.5\% are within the pore region). These observations bring into question how
-  one should define a pore in these types of systems. One usually measures a 
-  membrane's pore radius based on the size of a molecule it can reject, however
-  it is not clear where the edges of the pores are and what size molecule would
-  fit through. We leave these investigations for a future study.
+  ~\cite{zhou_supported_2005}. The system does not confine
+  sodium ions and head groups to just within the pore region. For dry systems,
+  19\% of sodium ions exist outside the pore region (except sandwiched, ordered basin,
+  where 16\% are outside the pore). Additionally, we see that in all cases, about 
+  3\% of the plotted tail density is located within the pore region (except ordered sandwiched,
+  where 1.5\% are within the pore region). For the solvated system, the results are similar,
+  however the head group density is shifted slightly radially outward. This is likely due to
+  swelling of the pore by water.
+
+%  These observations bring into question how
+%  one should define a pore in these types of systems. One usually measures a 
+%  membrane's pore radius based on the size of a molecule it can reject, however
+%  it is not clear where the edges of the pores are and what size molecule would
+%  fit through. We leave these investigations for a future study.
   %MRS7: or could say that the size could be different depending on the the nature of the molecle. Could bring up
@@
 
-  In all cases, the space in the pore region is filled with a mixture of 
-  sodium ions and head groups. The ordered parallel displaced configuration has
-  the highest density of sodium ions at the pore centers. Both the ordered and 
-  disordered parallel displaced configurations have higher concentrations
-  of head groups in the center. This observation highlights that the pore region
-  is dense, not hollow, and may impede transport of solvent and solutes. We 
-  observe how this changes when water is added to the system.
-  %MRS7: above: may impede compared to what?
-
-  %BJC6: lead with this vvv
-  In general, the composition of each region, particulary the pore region, is 
-  similar between all systems. We believe we can solvate and study transport in any
-  of the systems presented here and extract similar transport mechanisms. We will 
-  need to verify that this assumption is true.
-
-% BJC5 : I think this is making progress towards a better representation of these plots. I
-% outlined the tops of the bars on the histograms so the individual rdf don't get covered.
-% I think it helps. I also varied the thickness of the outlines so that the farthest back 
-% line is thickest. That way, when the outlines overlap, you can see the ones in front.
-%MRS7: looks weird, though - we should discuss more. Maybe just draw the tops of the histograms, and don't fill them in?
-%MRS7: maybe do as three figures across?
+  The space in the pore region is filled with a mixture of sodium ions
+  and head groups. The distributions appear somewhat different near r=0, but that noise 
+  is expected since there is significantly less sampling as r approaches 0. Regardless, 
+  all systems, including the solvated system, have a significant number of head groups 
+  and sodium ions occupying the pore center. This observation highlights that the pore
+  region is dense, not hollow, and may impede transport of solvent and solutes when
+  compared to the previous idealized picture of a hollow tube conducive to transport.
+
+  %BJC6: redone with only tops of histograms plotted, and water added
   \begin{figure}[!htb]
@@
   \end{subfigure}
-  %MRS7: lead with ``pretty much the same''
-  \caption{In all cases, the component radial distribution functions exhibit a
-	  composition gradient transitioning from the hydrophilic to the hydrophobic
-	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
-	  displaced (a), and sandwiched (b) configurations both show the highest
-	  concentrations of ions and head groups away from the pore center. Systems with
-	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
-	  concentrations of ions and head groups near the pore center, implying a more
-	  uniform, disordered pore.}~\label{fig:overlaid_densities}
+  \caption{In all cases, the component radial distribution functions are similar. 
+      They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
+	  regions. The biggest differences are at r=0 where noise is expected to be high due to 
+	  decreased sampling. The center of the pore is not hollow, but contains sodium ions and 
+	  head groups, even when the system is solvated. This architecture may impede transport in 
+	  the real system. The solvated system has a lower density of head groups near the 
+	  pore center which is likely due to the swelling that is necessary in order to fit water
+	  molecules in the pore region.}~\label{fig:overlaid_densities}
   \end{figure}
@@
 
-  We observe unusually slow dynamics in our system relative to other liquid crysal
-  %MRS7: are columnar liquid crystals the right comparison? Are these stickier? One could imagine that 
-  % energetic considerations in the LLCs smush them tighter together, which makes it harder for them to reorient. 
-  % in which case ours aren't atypical, but just not simulated long enough. 
-  systems. Typical diffusion constants for columnar liquid crystals have been reported
-  to be on the order of $10^{-11}~ m^2/s$ \cite{dong_translational_1984}. We measured the diffusion
-  constants of monomers in each of the systems we studied (See Table S-\ref{S-table:msd}) 
-  and learned that they are all on the order of $10^{-14}~m^2/s$.
-  Our systems may be frozen in a glassy state. It is also possible that we are simply 
-  observing characteristics of the experimental system. There has been no experimental work
-  done to study diffusion of Na-GA3C11 monomers in the Col\textsubscript{h}
-  system and no measurement of the glass transition temperature. Such a low
-  diffusion constant is not unheard of. A more recent study reported a diffusion
-  constant of $1.2\times10^{-14}~m^2/s$ for a different liquid crystal that
-  formed a hexagonal columnar phase \cite{dvinskikh_molecular_2002}.
+  % BJC6: edited to reduce comparison to other columnar LCs (and shortened)
+  We observe slow dynamics in our system. Typical diffusion constants for columnar
+  liquid crystals have been reported to be between $10^{-11}~ m^2/s$ 
+  \cite{dong_translational_1984} and $10^{-14}~m^2/s$ \cite{dvinskikh_molecular_2002}. 
+  We measured the diffusion constants of monomers in each of the systems we studied 
+  (See Table S-\ref{S-table:msd}) and learned that they are all on the order of 
+  $10^{-14}~m^2/s$. This is not entirely surprising considering how densely the 
+  monomers are packed as implied by diffraction experiments. The entangled tails 
+  likely restrict both vertical and lateral movement.
+
+%  Our systems may be frozen in a glassy state. It is also possible that we are simply 
+%  observing characteristics of the experimental system. There has been no experimental work
+%  done to study diffusion of Na-GA3C11 monomers in the Col\textsubscript{h}
+%  system and no measurement of the glass transition temperature. Such a low
+%  diffusion constant is not unheard of. A more recent study reported a diffusion
+%  constant of $1.2\times10^{-14}~m^2/s$ for a different liquid crystal that
+%  formed a hexagonal columnar phase \cite{dvinskikh_molecular_2002}.
 
@@
 %MRS5: let's talk about the implications of this (above); might want to move some of this into the SI.
+%BJC6: Which could be moved to supplemental? Theoretically, I could move most of the dihedral
+% stuff to SI and summarize briefly. But it I think it makes what we did more abstract.
 
@@
   The calculate value of ionic conductivity is 5x higher than experiment because 
-  we simulated infinitely long, aligned pores.
-%  The calculated values of ionic conductivity are higher than experiment by an
-%  order of magnitude. One can justify the reason for this result by considering
-%  the real system studied experimentally. 
-  The ionic conductivity measurement to which we are comparing was done with a
-  \SI{80}{\micro\metre} thick film, nearly 10,000 times thicker than our simulated
+  we simulated infinitely long, aligned pores. The ionic conductivity measurement 
+  to which we are comparing was done with a \SI{80}{\micro\metre} thick film, 
+  nearly 10,000 times thicker than our simulated
   system. The thick film is likely imperfectly aligned and has defects leading to
@@
 
-  \subsection{Effect of Crosslinking}\label{section:xlink}
-
-  We applied our crosslinking algorithm to equilibrated sandwiched and parallel
-  displaced configurations in the ordered pore basin. We allowed the crosslinking
+  \subsection{Effect of Cross-linking}\label{section:xlink}
+
+  We applied our cross-linking algorithm to equilibrated sandwiched and parallel
+  displaced configurations in the ordered pore basin. We allowed the cross-linking
   algorithm to propagate until greater than 90\% of vinyl groups were either involved
-  in a crosslinking reaction or were terminated. See section S\ref{S-section:xlink}
-  for further details on the crosslinking algorithm. We allowed the crosslinked
+  in a cross-linking reaction or were terminated. See section S\ref{S-section:xlink}
+  for further details on the cross-linking algorithm. We allowed the cross-linked
   configurations to simulate for 100 ns further in the NPT ensemble.
@@
   There are minor changes to the physical characteristics of these systems when 
-  they are crosslinked (See Figure ~\ref{fig:xlink}). The ionic conductivity of 
+  they are cross-linked (See Figure ~\ref{fig:xlink}). The ionic conductivity of 
   the sandwiched configuration decreases while that of the parallel displaced 
@@
   configuration and decreases in the parallel displaced configuration, however the 
-  values of crosslinked configurations fall within uncertainty of their un-crosslinked
+  values of cross-linked configurations fall within uncertainty of their un-crosslinked
   counterparts. The correlation length decreases in both systems, 
   %MRS7: from what to what?
+  %BJC6: If I say that, then shouldn't I say it for all metrics? That sounds
+  % a bit clunky especially when they are plotted in the figure and I just want to make
+  % somewhat general comments on the effect of cross-linking.
 but is most pronounced in the parallel displaced system.

### 2018-06-13 HII/Scripts/hbond_pairing.py

@@ -127,14 +127,14 @@ if __name__ == "__main__":
     fig1, ax1 = plt.subplots(2, 2)
     for i in range(2):
         for j in range(2):
-            ax1[i, j].plot(np.linspace(0, nlayers - 1, nlayers), np.mean(inter[(2*i + j)*nlayers:(2*i + j + 1)*nlayers, :], axis=1), linewidth=2)
+            ax1[i, j].plot(np.linspace(1, nlayers, nlayers), np.mean(inter[(2*i + j)*nlayers:(2*i + j + 1)*nlayers, :], axis=1), linewidth=2)
             ax1[i, j].text(.5, .85, 'Pore %d' % (1 + j + 2 * i), horizontalalignment='center', transform=ax1[i, j].transAxes, fontsize=14)
             ax1[i, j].set_ylim(0, 1)
 
     ax1[1, 0].set_xlabel('Layer', fontsize=14)
     ax1[1, 1].set_xlabel('Layer', fontsize=14)
-    ax1[0, 0].set_ylabel('Average interlayer\n hbonds', fontsize=14)
-    ax1[1, 0].set_ylabel('Average interlayer\n hbonds', fontsize=14)
+    ax1[0, 0].set_ylabel('Average shared\n hbonds', fontsize=14)
+    ax1[1, 0].set_ylabel('Average shared\n hbonds', fontsize=14)
 
     plt.tight_layout()
     plt.savefig('pore_hbonds.png')

### 2018-06-14 Ben_Manuscripts/structure_paper/Draft.tex
edits

@@
-\documentclass[journal=jpcbfk,manusciprt=article]{achemso}
-%\documentclass{article}
-%jpcbfk
+\documentclass[journal=jpcbfk,manuscript=article]{achemso}
 
@@
   closely reproducing the experimental pore structure requires a carefully 
-  constructed initial configuration in order to avoid falling into a metastable
-  basin. We use simulated X-ray Diffraction (XRD) patterns in order to ensure 
+  constructed initial configuration in order to avoid falling into metastable
+  basins. We use simulated X-ray Diffraction (XRD) patterns in order to ensure 
   maximum consistency between our structures and experiment. We show that pores 
@@
   pattern due to asymmetries introduced by hydrogen bonds between monomer head
-  groups and water molecules. We explore, in depth, the composition and 
-  structure of the nanopores and reveal that there exists a composition gradient
-  rather than a hard partition between the hydrophilic and hydrophobic regions.
-  The clearer picture of the nanoscopic structure of these membranes provided in
+  groups and water molecules. We explore the composition and structure of the 
+  nanopores and reveal that there exists a composition gradient rather than a 
+  hard partition between the hydrophilic and hydrophobic regions. The clearer 
+  picture of the nanoscopic structure of these membranes provided in
   this study will enable a better understanding of the mechanisms of small 
@@
 
-  More highly selective membranes would be extremely useful for the recovery of valuable
-  products from complex aqueous and organic solutions. For example, flowback
-  water (FW) produced during hydraulic fracturing is a complex wastewater full of
-  potentially valuable dissolved organic compounds such as acetate
-  \cite{dischinger_application_2017}. There is increasing pressure to reuse
-  hydraulic fracturing water rather than dispose of it in order to reduce social
-  and environmental impacts as well as cost \cite{theodori_hydraulic_2014}.
-  Rather fully than dispose of the wastestream generated in the recycling
-  process, we can instead use highly selective membranes in order to successfully
-  recover useful compounds.
+  More highly selective membranes would be extremely useful for the recovery of 
+  dissolved species in complex aqueous and organic solutions. For example, selective
+  membranes can further progress forward osmosis processes by reducing the cost of 
+  separating potable water from draw solutions~\cite{mccutcheon_novel_2005}. Additionally, 
+  flowback water (FW) produced during hydraulic fracturing is a complex wastewater full
+  of potentially valuable dissolved organic compounds such as acetate 
+  that can be recovered using highly selective membranes \cite{dischinger_application_2017}.
+  Finally, a significant amount of nitrogen and phosphorus from fertilizer is found in 
+  wastewater. Selective membranes offer a route towards low energy nutrient recovery 
+  from these wastewaters which can help sustain fertilizer production and subsequently
+  food production into the future \cite{xie_membrane-based_2016}.
+  % as we near peak production of minable phosphorus rock .
+
+%  There is increasing pressure to reuse
+%  hydraulic fracturing water rather than dispose of it in order to reduce social
+%  and environmental impacts as well as cost \cite{theodori_hydraulic_2014}.
+%  Rather fully than dispose of the wastestream generated in the recycling
+%  process, we can instead use highly selective membranes in order to successfully
+%  recover useful compounds.
 
@@
   Current commercial RO and NF membranes suffer limitations to their selectivity
-  which is inherent to their fabrication. Although scalable, each of these two types
-  of membranes has a degree of stochasticity that makes overcoming well-known the 
+  because they are unstructured. Although scalable, their fabrication involves the 
+  spontaneous assembly of polymers into disordered structures which offer separation 
+  pathways that are tortuous and polydisperse in size. This makes overcoming the well-known 
   permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
-  the permeability of a desired molecular or atomic species, while maintaining the same 
-  retention of an undesired species \cite{werber_materials_2016}.
+  the permeability of a desired molecular or atomic species, while maintaining the 
+  same retention of an undesired species \cite{werber_materials_2016}.
 
@@
   have the ability to self-assemble into porous nanostructures
-  \cite{smith_ordered_1997} which can be crosslinked to create mechanically
+  \cite{smith_ordered_1997} and can be crosslinked to create mechanically
   strong membrane films with pores on the order of 1 nm in diameter
@@
   in solution. The membrane gains a net surface charge when counterions from the head
-  groups that line the pore walls escape into the feed solution in order to balance 
+  groups that line the pore walls escape into the feed solution in an effort to balance 
   the gradients of concentration and electric potential \cite{donnan_theory_1995}.
@@
   and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
-  phases (See Figure~\ref{fig:bcc_v_hII}). When separating organic solutes from
-  NaCl, Q\textsubscript{I} phase membrane filtration experiments have shown
-  selectivity 2--3 times higher than commercial RO and 6--12 times higher than
-  commercial NF membranes \cite{dischinger_application_2017}.  When separating a
-  series of various sized dyes, the H\textsubscript{II} phase membrane showed
-  complete rejection of dyes bigger than 1.2 nm in size \cite{zhou_supported_2005}.
+  phases. When 
+  separating organic solutes from NaCl, Q\textsubscript{I} phase membrane filtration
+  experiments have shown selectivity 2--3 times higher than commercial RO and
+  6--12 times higher than commercial NF membranes \cite{dischinger_application_2017}.
+  When separating a series of various sized dyes, the H\textsubscript{II} phase membrane
+  showed complete rejection of dyes bigger than 1.2 nm in size \cite{zhou_supported_2005}.
 
@@
   literature, has been referred to as the Col\textsubscript{h} thermotropic
-  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}). 
+  phase\cite{feng_scalable_2014}. 
   % BJC6: maybe not a necessary detail
@@
   In 2016, Feng et al. showed that one could obtain the same result using a second
-  technique termed soft confinement\cite{feng_thin_2016}. Current efforts are focused
-  on extending the method to the H\textsubscript{II} phase and characterizing the 
-  performance of these newly aligned systems.
+  technique termed soft confinement\cite{feng_thin_2016}. Current experimental 
+  efforts are focused on extending the method to the H\textsubscript{II} phase 
+  and characterizing the performance of these newly aligned systems.
 
@@
 % columns instead?
+% BJC6 : I will get to redo-ing this. Just takes some time to refamiliarize myself with
+% the software I used to create it
   \begin{figure}
@@
 
-  Our current understanding of the molecular details of LLC membrane nanostructure
+  Our current understanding of the molecular details of LLC membranes' nanostructure
   is not sufficient to be able to precisely design them for specific separations. 
@@
   structural modifications. Resel et al.~varied the length of the monomer tails and the
-  counterion used and observed its affect on pore spacing \cite{resel_structural_2000}.
+  counterion used and observed its effect on pore spacing \cite{resel_structural_2000}.
   In a later study of rejection performance, it was shown that membranes formed by cross-
@@
   systems have been macroscopic models that likely do not adequately describe
-  transport at these length scales \cite{hatakeyama_water_2011}. 
-  %MRS7: maybe a pass at this?
-  Modeling with molecular detail could provide sufficient information about the mechanisms 
-  and chemical features to better inform experimental design of similar nanostructured membranes. 
-  %It will be
-  %challenging to efficiently narrow down the large design space in a laboratory
-  %setting without a robust model.
-
-  %MRS7: changing future tense to present tense here.
-  A molecular-level understanding of LLC polymer membrane structure, enabled by
+  transport at these length scales \cite{hatakeyama_water_2011}. Modeling with molecular
+  detail could provide sufficient information about the mechanisms and chemical features
+  to better inform experimental design of similar nanostructured membranes.
+
+  A molecular-level understanding of LLC membrane structure, enabled by
   molecular dynamics (MD) simulations, can provide guidelines to reduce the large
@@
   from molecular dynamics simulations can provide the required level of detail
-  (Fig. \ref{fig:detail}), assuming the force fields are sufficiently accurate.
+  (Figure \ref{fig:detail}), assuming the force fields are sufficiently accurate.
   With such an atomistic model, we can directly observe molecular-level solute
@@
 
+  %BJC6: is this too bold considering the work done at University of Wisconsin?
   In this study, we build a significantly more realistic atomistic model of LLC
@@
 	space periodic spacing of 7.4 \AA~. Since this reflection corresponds to double
-	the spacing of R-$\pi$ in real space, will refer to this reflection as R-double. 
+	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
 	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
@@
 	respective quadrants. In many liquid crystal systems one can explain the spots
-	as the tilt angle of the alkane chains with respect to the membrane
+	as the product of alkane chains tilted with respect to the membrane
 	plane\cite{govind_simple_2001}.
@@
 	related the distance between pores. The feature, which we named R-pores, is
-	characterized by dots along the equatorial axis defined when $q_z$ = 0. The
+	characterized by dots along the equatorial axis defined by $q_z$ = 0. The
 	spacing between dots is indicative of the hexagonal symmetry of the packed
@@
         \end{subfigure}
-        %MRS7: picture says R-helix still.
 	\caption{(a) (Reproduced from \citenum{feng_thin_2016}) The repeat spacing
@@
 	hydrophilic regions where transport is likely to occur. One may instinctively imagine these 
-	regions as tube-like pathways with well-defined boundaries. We will explore the composition
+	regions as tube-like pathways with well-defined boundaries. We explored the composition
 	of the pores, the partition between the hydrophilic and hydrophobic regions, and its 
@@
 	ambient water may be leached into the system. The hydrogen bonding network formed by the 
-	water may play a role in structuring the pore. We used simulated X-ray diffraction patterns
+	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
 	to see if there is any meaningful structural difference between a "dry" and "wet" system.
@@
   configuration from the trajectory which we used for full system
-  construction (Figure~\ref{fig:python}a). See section S-\ref{S-section:parameterization} 
+  construction (Figure~\ref{fig:python}a). See section S\ref{S-section:parameterization} 
   for further detail.
@@
   \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system (See section S~\ref{S-section:self_assembly}). 
-  %BJC5: section showing self-assembly set up to be added
+  indicators of progress towards an ordered system (See section S\ref{S-section:self_assembly}). 
   To bypass the slow self-assembly process, we use Python scripts to assemble monomers
@@
   continuity along the pore axis, avoiding any edge effects and creating an
-  infinite length pore ideal for studying transport. We prefer a small number stacked
+  infinite length pore ideal for studying transport. We prefer a small number of stacked
   monomers in order to reduce computational cost and to allow us to look at
@@
   per column in order to obtain sufficient resolution when simulating
-  X-ray diffraction patterns. %This point will be explained in more detail later.
+  X-ray diffraction patterns (see further discussion in section S\ref{S-section:monomers_per_column}).
   %MRS7: refer to supporting information (if it's there) for more discussion on stability as a function of height?
+  %BJC6: gave it a shot in supplemental
 
@@
   of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
-  Supporting information, section S-\ref{S-section:initial_config_dependence}. The 
+  Supporting information, section S\ref{S-section:initial_config_dependence}. The 
   distance between vertically stacked monomers, the position of monomers with respect 
@@
   on R-$\pi$ and then allowed the system to readjust during equilibration. Each monomer was
-  rotated so the plane of its aromatic head groups would be coplanar with the xy plane. We
+  rotated so the plane of its aromatic head group would be coplanar with the xy plane. We
   explored three different initial monomer spacings. The first is exactly
@@
   \AA. However this spacing yields non-physical behavior which is detailed in the 
-  Supporting Information, section S-\ref{S-section:initial_dbwl}.
+  Supporting Information, section S\ref{S-section:initial_dbwl}.
 
@@
   is inconsistent with R-$\pi$. It is also infeasible for the monomers to orient in the 
-  T-shaped conformation because of the bulky tail groups. We will explore the system's 
+  T-shaped conformation because of the bulky tail groups. We explored the system's 
   preference towards the sandwiched vs. parallel displaced stacking modes in some detail.
@@
   head groups in the parallel displaced initial configuration stack with an offset
-  of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See the Supporting
-  Information, Figure~\ref{S-fig:stacking} for a detailed illustration of the initial
-  configurations in each mode.
+  of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See Figure 
+  S~\ref{S-fig:stacking} for a detailed illustration of the initial configurations in each mode.
 
@@
   (\ref{point:monomernum}). We tested configurations constructed with a varied
-  number of columns per pore. We built systems in the offset and parallel
+  number of columns per pore. We built systems in the sandwiched and parallel
   displaced configurations with 4, 5, 6, 7 and 8 monomers per layer.
@@
   %MRS7: could put this mostly in supporting. 
-  We developed equilibration schemes to create dry and wet configurations. Both
+  %BJC6: cut in half
+  We developed equilibration schemes for creating dry and wet configurations. Both
   schemes start with an initial configuration generated according to the previous
-  guidelines. To create a dry configuration, we fix monomer head groups in the
-  sandwiched or parallel-displaced configuration using position restraints with a
-  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in
-  the NVT ensemble which allows the monomer tails to settle without disrupting
-  the ordering of the head groups. Doing so also mitigates system dependence on
-  initial monomer configuration. Every 50 ps, we reduce the force constants by
-  the square root of its previous value. Once the force constant is below 10 KJ
-  mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
-  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
-  unrestrained structure to equilibrate for 5 ns in the NPT ensemble
-  with pressure controlled by the berendsen barostat. Next, we run long NPT
-  equilibration simulations for at least 400 ns using the Parrinello-Rahman
-  barostat with a time constant of 10 ps.
-
-  % MRS6: some parameters missing here (time run between insertions, etc). 
-  % I assume they are in supporting information?
-  % BJC5: all water is present in initial configuration. This did not follow the more
-  % complex procedures that I've come up with since then. 
-  In order to create a ``wet'' system, we solvated an initial configuration with
-  water using \texttt{gmx solvate}. We remove all water molecules placed outside
-  the pore region. Then we randomly remove water molecules inside the pore region
-  until the pores reach the desired concentration of water. The remainder of the
-  equilibration follows the same procedure as the dry system.
+  guidelines. For wet systems, the desired concentration of water was added to 
+  the initial configuration and we carried out equilibration in the same way
+  as the dry systems. First, we fixed monomer head groups in place using position
+  restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We gradually
+  released the position restraints by decreasing the force constants over a series
+  of simulations. We allowed the resulting unrestrained structure to equilibrate for
+  5 ns in the NPT ensemble with pressure controlled by the berendsen barostat 
+  followed by NPT equilibration simulations run for at least 400 ns using the 
+  Parrinello-Rahman barostat. More precise details are available in 
+  section S~\ref{S-section:equilibration}.
 
@@
 
-  Using equilibrated structures, we carry out various calculations to
-  characterize the system. We define the point at which a system is equilibrated
-  based on when the distance between pores stops changing.  We determined when
+  Using equilibrated structures, we carried out various calculations to
+  characterize the system. We defined the point at which a system is equilibrated
+  based on when the distance between pores stopped changing.  We determined when
   the distances stopped changing by applying the statistical test,
@@
   \cite{chodera_simple_2016,shirts_statistically_2008}. Typically, the pore-to-pore
-  distance equilibrates between 200 and 350 ns. We used data collected after 
+  distance equilibrated between 200 and 350 ns. We used data collected after 
   equilibration to do all subsequent analysis.
@@
   %BJC5: moved to supporting info
+  %BJC6: Do you think I should add this back since I used nematic order parameter to
+  % differentiate between ordered/disordered basins?
 %  \subsubsection{\textit{The nematic order parameter}}\label{method:nematic_order}
@@
   where A is a fitting parameter for amplitude, z is the independent variable of $g(z)$ 
-  and L is the fit correlation length. The error in the estimated value of L is 
-  calculated as the square root of the diagonal entry of the covariance matrix of 
+  and L is the fit correlation length. We calculated the error in the estimated value
+  of L as the square root of the diagonal entry of the covariance matrix of 
   optimized fit parameters.
@@
   This function could be used in place of Equation~\ref{eqn:decaying_exponential}, however
-  it does not fit the peaks of $g(z)$ from parallel displaced configurations well enough
-  to extract a reliable value of L.
+  it does not consistently fit the peaks of $g(z)$ from parallel displaced configurations 
+  well enough to extract a reliable value of L.
   %BJC5: maybe include plots of these fits in supporting info
@@
   carbon atoms making up the monomer tails. We binned the radial distance of all
-  atoms in each group from the pore centers, then normalized by the volume of the
-  annulus defined by the bin edges and the z box vector (See Figure~\ref{S-fig:rdf_diagram}
-  in the Supporting Information).
+  atoms in each group from the pore centers, then normalized by the area of the
+  annulus defined by the bin edges and the z box vector (See Figure~S\ref{S-fig:rdf_diagram}).
 
@@
 
-  Simulated X-ray diffraction patterns were generated based on atomic
-  coordinates in order to make a direct experimental comparison. All atomic
-  coordinates were simulated as Gaussian spheres of electron density
-  corresponding to each atom's electronic radius. A three dimensional Fourier
-  transform (FT) of the array of electron density results in a three dimensional
+  We generated simulated XRD patterns based on atomic coordinates in order to make
+  a direct experimental comparison. We modelled all atomic coordinates as Gaussian
+  spheres of electron density corresponding to each atom's electronic radius. A 
+  three dimensional Fourier transform (FT) of the array of electron density results in a three dimensional
   structure factor which represents the unit cell in reciprocal space. The
@@
   pores were oriented perpendicular to the direction of the incident X-ray beam. 
+  %BJC6: Below is the part I'm having a hard time putting into words. 
   Although the pores were vertically aligned, the crystalline domains were still
@@
   We calculated the average intensity within R-alkanes of the experimental pattern,
-  $I_{avg}$ and divide all intensities by this values. In this way, the average intensity
-  of the alkanes is equal to 1. When calculating $I_{avg}$, we excluded intensities 
+  $I_{avg}$ and divided all intensities by this value. In this way, the average intensity
+  of R-alkanes was equal to 1. When calculating $I_{avg}$, we excluded intensities 
   within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the simulated
   patterns differ from experiment in those regions in all cases. Specifically, in contrast
-  to the experimental WAXS pattern, R-$\pi$ appearing in simulated diffraction patterns 
-  intersects with R-alkanes (See Fig. \ref{fig:XRDsim}). We set
+  to the experimental WAXS pattern, R-$\pi$ as it appears the simulated diffraction 
+  patterns intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set
   an upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$. 
   Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored uniformly. 
-  We apply the same scaling method to the simulated patterns. We carefully chose a scaling
-  factor of $f=3.1$ in order to visibly display all features in the all patterns.
+  We applied the same scaling method to the simulated patterns. We carefully chose a scaling
+  factor of $f=3.1$ in order to visibly display all features in all patterns.
 
@@
 
-  %BJC5: perhaps this paragraph should be moved to supporting info.
-  %MRS7: probably?  Describing the _idea_ of the procedure can be in
-  %main paper, but perhaps more details of the procedure in the supporting info.
-
-  We developed the algorithm based on the known reaction mechanism.
-  Cross-linking of this system is a free radical polymerization (FRP) taking
-  place between terminal vinyl groups present on each of the three monomer tails.
-  The reaction mechanism is drawn out in Figure S-\ref{S-fig:xlink_mech}.
-  FRPs require an initiator which bonds to the system, meaning new atoms are
-  introduced into the system. For simplicity, we simulated the initiator as
-  hydrogen and made it present in the simulation by including them as dummy atoms
-  in all possible locations where an addition could occur. We carry out the
-  cross-linking procedure iteratively. During each iteration, the algorithm
-  selects eligible bonding carbon atoms based on a distance cut-off. The topology
-  is updated with new bonds and dummy hydrogen atoms are changed to appropriate
-  hydrogen types.  Head-to-tail addition was the only propagation mode considered
-  due to its dominance in the real system \cite{young_introduction_2011}. We did
-  not consider direction of attack because the resultant mixture is racemic.
-
-  Our implementation requires long simulation times to achieve high cross-link 
-  densities. A typical cross-linking procedure can take up to 24 hours. In
-  order to collect equilibrated data, further NPT simulation is necessary. We
-  typically run a cross-linked system for an additional 100 ns to allow the system
-  to readjust. For those reasons we did not cross-link all systems tested, but only
-  the most promising structures. We show that cross-linking does not significantly
-  change any of our drawn conclusions in Section 3.6.
+  We based our cross-linking algorithm on the known reaction mechanism 
+  (Figure S\ref{S-fig:xlink_mech}). The reaction takes place at the terminal vinyl groups
+  on each alkane tail. The procedure is carried out iteratively. Each iteration, the
+  algorithm chooses carbons to cross-link based on the distance between eligible 
+  carbon pairs. The algorithm then updates the topology with the new bonds and atom
+  types, energy minimizes the system and runs a short simulation before selecting 
+  the next group of eligible carbons atoms.
 
@@
   to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
-  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional systems with
-  monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
+  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional 
+  systems with monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
   of the supporting info for more details on sensitivity to initial layer spacing). 
@@
 
+  \begin{figure}[!htb]
+	\centering
+	\includegraphics[width=\linewidth]{p2p.png}
+	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
+			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
+			 increases as the number of columns in each pore increases.}~\label{fig:p2p}
+  \end{figure}
+
   All systems tested, although equilibrated from the perspective of the metrics used here, are
   frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
-  we are trying to match. In the limit of infinite simulation time, all systems will in theory converge to
-  a single equilibrium configuration, but that time is far beyond the 100's of nanosecond simulated here. 
-  For simplicity, we 
-  %MRS7: tenses
-  group the systems studied here into the ordered and disordered basins. Any system where 
-  $\mathit{d}=3.7$ \AA~will be included in the
+  we are trying to match. In the limit of infinite simulation time, all systems will in theory 
+  converge to a single equilibrium configuration, but that time is far beyond the 100's of 
+  nanosecond simulated here. For simplicity, we group the systems studied here into the ordered
+  and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
   ordered basin and any system where $\mathit{d}=5.0$ \AA~will be included in the disordered basin.
-  The reason for these names will become clearer as we progress through our analysis.
+  Generally, when monomers are started further apart, they stay further apart than systems where
+  monomers are started closer together (see Table~\ref{table:correlation_length}). Because of the
+  extra space between stacked monomers, monomer head groups have more rotational freedom. We
+  quantified the ordering of the head groups using the nematic order parameter (See section S~\ref{method:nematic_order}). 
+  Disordered basin systems have a lower nematic order parameter (meaning they are more disordered) 
+  than ordered basin systems.
+
   %MRS7: maybe above say where (i.e.
@@
   %BJC5: thesis needs rewording.
-  %MRS7: probably, since the disorered - 6 are close to the experimental distances.  Is it accurate to say
-  %that they don't have the experimental structural features? 
-  Disordered basin systems built with 6 columns-per-pore are not compact in the z-direction.
-  The final pore spacing is close to experiment within its uncertainty. Relative to ordered basin 
-  6 column-per-pore systems, the unit cell is elongated in its z dimension and contracted in its
-  x and y dimensions, however the box volume stays nearly constant in all cases 
-  (Figure~\ref{fig:box_dimensions}). The system is likely not fully equilibrated and may eventually
-  rearrange into something that resembles a 5 column-per-pore system. Further investigations 
-  into this are beyond the scope of this paper.
-
-  \begin{figure}[!htb]
-	\centering
-	\includegraphics[width=\linewidth]{p2p.png}
-        %MRS7: need to deal with the fact that layer-6, more disordered are within error of 4.12
-        %MRS7: I think the answer is that the equilibrated distance is much bigger. you talk about the INITIAL distance being bigger, but I think you also need to emphasize that it stays there.
-	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
-			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
-			 increases as the number of columns in each pore increases.}~\label{fig:p2p}
-  \end{figure}
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=\textwidth]{box_dimensions.png}
-  %MRS7: not really clear from the caption why this is shown.
-  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5~\AA~$), the unit cell
-  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
-  constant across all cases. The y dimension box vectors are not included since we use 
-  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
-  \end{figure}
-
-  \subsection{Structural refinement with 2D WAXS data}
+  Monomers in disordered basin systems built with 6 columns-per-pore stack too far apart.
+  Those in the disordered sandwiched and disordered parallel displaced configurations stack 
+  $\approx$ 4.87 and 4.94~\AA apart respectively, which is ca. 1.2~\AA further apart than 
+  suggested by experiment. 5 column-per-pore systems stack, at a maximum, 0.9 ~\AA further
+  apart than experiment (see Table~\ref{table:correlation_length}). Methodology for calculating
+  equilibrium stacking distance is fully explained in section~\ref{section:rpi}.
+
+%  Relative to ordered basin 
+%  6 column-per-pore systems, the unit cell is elongated in its z dimension and contracted in its
+%  x and y dimensions, however the box volume stays nearly constant in all cases 
+%  (Figure~\ref{fig:box_dimensions}). The system is likely not fully equilibrated and may eventually
+%  rearrange into something that resembles a 5 column-per-pore system. Further investigations 
+%  into this are beyond the scope of this paper.
+
+%  \begin{figure}[!htb]
+%  \centering
+%  \includegraphics[width=\textwidth]{box_dimensions.png}
+%  %MRS7: not really clear from the caption why this is shown.
+%  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5~\AA~$), the unit cell
+%  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
+%  constant across all cases. The y dimension box vectors are not included since we use 
+%  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
+%  \end{figure}
+
+  \subsection{Simulated XRD comparison to 2D WAXS data}
 
@@
   displaced and sandwiched configurations at 300 K in the ordered and disordered
-  basins. We extended each simulation by 100 ns in order to get more equilibrated 
-  data. 
-  %MRS7: sentence above reads strangely. Was ``more'' sufficient? what criteria was used to stop at 10?
-We generated simulated patterns using the extended simulation trajectories.
-  The patterns for all structures are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
-
-  % BJC5: I think something like this has to go somewhere.
+  basins. We generated simulated patterns using the equilibrated portion of each 
+  simulation trajectory. The patterns for all structures are shown and compared to
+  experiment in Figure~\ref{fig:XRDsim}.
+
   The diffraction patterns show some noise, especially along the axis where $q_r$=0. There are
   two main reasons for this noise. First is that we angle averaged the 3D structure factor 
-  (see section~\ref{method:xrd}) which inherently gives less data as q approaches 0. Second, 
+  (see section~\ref{method:xrd}) which inherently gives less data as $q_r$ approaches 0. Second, 
   our simulations are not long enough to sample enough truly independent configurations within
@@
   we can suppress some of the noise (See section S\ref{S-section:xrd_noise}).
- %MRS7: two things going on - they are not smooth because of lack of sampling WITHIN the metastable basin (somewhere in there mention angle averaging leads to less data at q=0 than anywhere else, but this is separate from being truly independent, which would mean totally converged in the equilibrium ensemble (i.e.
-reaching a single equilibrium ensemble in the >miliseconds timescale)
-
-%  Increasing the number of trajectory frames used to simulate the structure factor within
-%  a given interval of time does not offer any improvement.
-%MRS7: not sure what you mean above. Increasing the frequency of frames used? 
-%BJC6: yes, since the frames are just more snapshots of non-independent configurations. I think this is already implied above.
-
-  %BJC5: put figure letters in upper left hand corner of each pattern.
+
   \begin{figure}[!htb]
@@
 		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
-			        %\caption{Sandwiched}~\label{fig:rzplot_layered_300K}
 			\end{subfigure}
@@
 	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
-	        		%\caption{Disordered sandwiched}~\label{fig:rzplot_layered_300K}
 			\end{subfigure}
@@
 	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
-	        		%\caption{Experimental WAXS}~\label{fig:offset_tails}
 			\end{subfigure}
@@
 		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
-			        %\caption{Parallel displaced}~\label{fig:rzplot_offset_300K}
 			\end{subfigure}
@@
 			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
-			        %\caption{Disordered parallel displaced}~\label{fig:rzplot_offset_300K_disordered}
 			\end{subfigure}
@@
 	\end{subfigure}	
-        %MRS7: be consistent on capitalization
-	\caption{Simulated X-ray diffraction patterns show some qualitative agreement with 
-	experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
-	disordered basin (d) Parallel Displaced, ordered basin and (e) Parallel Displaced, disordered basin 
-	configurations with (c) experimental WAXS. Quantitative comparisons of the relative 
-	intensities of reflections of interest are present in Table~\ref{table:relative_inensities_300K}. 
-	In all cases, R-double is not present.}~\label{fig:XRDsim} 
-        %MRS7: may need to make clearer the differences between the simulated structures. I think its worth pointing out
-        %that although rdouble isn't there, for the more structured ones, there is a 7.4 band, even if it disappears at q=0.
-        %BJC6: 7.4 band is any parallel displaced configuration, not more structured systems.
+	\caption{Simulated XRD patterns show some qualitative agreement with experiment. Shown is a 
+	comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
+	disordered basin (d) Parallel displaced, ordered basin and (e) Parallel displaced, disordered basin 
+	configurations with (c) experimental WAXS. 	In all cases, R-pores, R-alkanes and R-$\pi$ are 
+	present to some degree. R-spots is also present, however it is generally partially covered by the
+	broad R-$\pi$ reflection. Quantitative comparisons of the relative intensities of reflections of
+	interest are presented in Table~\ref{table:relative_inensities_300K}. In both XRD patterns generated
+	from parallel displaced patterns, there is a faint line across $q_z \approx 0.7~$\AA$^{-1}$, half
+	the simulated value of R-$\pi$. Although it does not cross through $q_r = 0$~\AA$^{-1}$, it is at 
+	the same $q_z$ value where we expect R-double to be present. Still, R-double is not fully reproduced
+	in any of the simulated patterns.}~\label{fig:XRDsim} 
   \end{figure}
@@
   $q_r = 0~\AA^{-1}$ so it does not necessarily appear for the same reason as R-double. 
-  This type of pattern is characteristic of a helix (reference something).
-  %BJC5: reference something like a dna diffraction paper
+  This type of pattern is characteristic of a helix ~\cite{watson_structure_1953}. The 
+  head groups in the parallel displaced configuration are arranged in a helix.
   It is possible that these reflections contribute to the diffuse reflections that connect
@@
   our membrane system, simulated at 300K, does not fully represent the true structure at 300K.
-
-  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
-  is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
-  The relative intensity of R-spots is slightly higher than in experiment (1.5 vs. 1.3). R-double 
-  is still not present. We will use the system simulated at 280K to more thoroughly explore the 
-  origin of R-spots.
-
-  \begin{figure}[!htb]
-	  \begin{subfigure}{0.45\linewidth}
-	  	\centering
-	  	\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
-	  	\caption{}
-	  \end{subfigure}
-	  \begin{subfigure}{0.45\linewidth}
-	  	\centering
-	  	\includegraphics[width=\linewidth]{rzplot_layered_280K_jet.png}
-	  	\caption{}\label{fig:sandwiched280K}
-	  \end{subfigure}
-  \caption{R-spots increases in intensity when the temperature of the system is lowered to 280K.
-  In this case, the simulated R-spots is more intense than experiment.}
-  %MRS7: slightly more than experiment; 1.3 and 1.5 are pretty comparable given the scale of other things.
-  %MRS7: a and b aren't explained. 
-  \end{figure}
-
-  Evidence strongly suggests that the R-spots signal is not a result of alkane chain tilt. Previous literature
-  has attributed the spots in this particular WAXS pattern as the product of tilted alkane
-  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched configuration simulated
-  at 280K. We measured the tilt angle of the alkane chains and showed that our system 
-  equilibrates to an average tilt angle of -2\degree (Fig.~\ref{fig:tilt}).
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
-  \caption{We measured the angle made between each monomer alkane tail and the
-	  membrane plane. The average tilt angle (dashed line) is near -2\degree~which is far from 
-	  the 37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
-  \end{figure}
-
-  To understand the origin of R-spots, we determined which
-  atoms gave rise to the feature. Since R-spots is present as higher intensity
-  spots within R-alkanes, it is likely that the spots arise as a consequence of
-  the tails. By removing all non-tail atoms from the trajectory and simulating a
-  diffraction pattern with the remaining atoms, we were able to isolate the cause of 
-  the spots to the tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
-  the centroids of the tails (Figure S\ref{S-fig:centroids}) and measured the angle
-  between each centroid and its nearest neighbors with respect to the plane of the 
-  membrane. We see distinct peaks in the distribution of these angles 
+  Lowering the temperature to 280K helped us to better resolve R-spots. 
+%  The relative intensity 
+%  of R-spots in this system is slightly higher than experiment (1.5 vs. 1.3)
+
+%  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
+%  is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
+%  The relative intensity of R-spots is slightly higher than in experiment (1.5 vs. 1.3). R-double 
+%  is still not present. We will use the system simulated at 280K to more thoroughly explore the 
+%  origin of R-spots.
+
+  Evidence strongly suggests that the R-spots signal is not a result of alkane chain tilt. 
+  Previous literature has attributed the spots in this particular WAXS pattern as the product 
+  of tilted alkane chains~\cite{feng_scalable_2014}. We measured the tilt angle of the
+  alkane chains of the 280K system and showed that it equilibrates to an average tilt angle of
+  -2\degree (Fig.~\ref{fig:tilt}), far from the 37\degree tilt angle previously used to 
+  explain R-spots.
+
+  To understand the true origin of R-spots, we determined which atoms gave rise to the 
+  feature. Since R-spots is present as higher intensity spots within R-alkanes, it is
+  likely that the spots arise as a consequence of the tails. By removing all non-tail atoms
+  from the trajectory and simulating a diffraction pattern with the remaining atoms, we were
+  able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the 
+  tails stay nearly flat, we plotted the centroids of the tails (Figure \ref{fig:centroids})
+  and measured the angle between each centroid and its nearest neighbors with respect to the 
+  plane of the membrane. We see distinct peaks in the distribution of these angles 
   (Figure~\ref{fig:tail_packing}).
@@
   are located at $\pm 33 \degree$ which is the same location where the highest
-  intensity of spots are located on the simulated patterns. We confirmed this 
+  intensity of spots are located in the simulated patterns. We confirmed this 
   by radially integrating the 2D WAXS pattern for 
@@
 
-%MRS7: a thought - moving some of figures 10,11,12 together with some subfigures, since they all communicate the same idea.
-%11a is probably unneeded.
+%BJC6: figures are in order that they are talked about in text.
   \begin{figure}[!htb]
-	\centering
-	% remove first picture for now
-	\begin{subfigure}{0.45\linewidth}
-		\centering
-	 	\vspace{-2em}
-		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
-		\caption{}\label{fig:topdown_tails_only}
-	\end{subfigure}
-	\begin{subfigure}{0.45\linewidth}
+  \begin{subfigure}{0.32\linewidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.png}
+  	\caption{}\label{fig:sandwiched280K}
+  \end{subfigure}
+  \begin{subfigure}{0.32\linewidth}
+    \includegraphics[width=\textwidth]{tilt_dist.png}
+    \caption{}\label{fig:tilt}
+  \end{subfigure}
+  \begin{subfigure}{0.32\linewidth}
 	\centering
@@
   \end{subfigure}
-	\caption{(a) We removed all atoms except carbon atoms that constitute the tails from a 
-	sandwiched configuration trajectory. (b) The simulated XRD pattern of the
-        tail-only trajectory still shows R-spots}\label{fig:tails}
-  \end{figure}
-
-%  \begin{figure}[!htb]
-%  \centering
-%  	\begin{subfigure}{\linewidth}
-%	\centering
-%		\begin{subfigure}{0.45\textwidth}
-%        		\centering
-%        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
-%        		\caption{}~\label{fig:offset_tails}
-%		\end{subfigure}
-%		\begin{subfigure}{0.45\textwidth}
-%		\centering
-%	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
-%		        \caption{}~\label{fig:offset_integration}
-%		\end{subfigure}
-%	\end{subfigure}
-%	\begin{subfigure}{\linewidth}
-%	\centering
-%		\begin{subfigure}{0.45\textwidth}
-%	        \centering
-%		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
-%		        \caption{}~\label{fig:layered_tails}
-%		\end{subfigure}
-%		\begin{subfigure}{0.45\textwidth}
-%        	\centering
-%		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
-%		        \caption{}~\label{fig:layered_integration}
-%		\end{subfigure}
-%	\end{subfigure} 
-%  \caption{We hypothesize that R-spots is the result of ordered tail packing.
-%	  Defining the membrane plane to be 0\degree, we measured the angles between each
-%	  alkane chain tail centroid and its nearest neighbor centroids for the
-%	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
-%	  that appear in each distribution are centered near $\pm~33\degree$. We radially
-%	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
-%	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
-%	  Peaks appear in the same location as the angle distributions which corroborates
-%	  our hypothesis. Further, we note that the peaks are strongest in both plots
-%	  associated with the sandwiched configuration. As shown in Figure
-%	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
-%	  more intense R-spots reflections. Note that plots of integrated intensity are
-%	  normalized so the average alkane intensity (excluding reflections $\pm
-%	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
-%	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
-%  \end{figure}
-
-  % BJC4: modification of above figure to only included sandwiched data. The rest can go
-  % in supporting info.
-  \begin{figure}[!htb]
-  \centering
-	\begin{subfigure}{\linewidth}
-	\centering
-		\begin{subfigure}{0.45\textwidth}
+  %BJC6: Brought this back to make 6 figures.
+  \begin{subfigure}[t]{0.32\linewidth}
+    \centering
+	\includegraphics[width=\textwidth]{centroids_box.png}
+  \caption{}\label{fig:centroids}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.32\linewidth}
         \centering
@@
   \end{subfigure}
-		\begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}[t]{0.32\textwidth}
         	\centering
@@
   \end{subfigure}
-	\end{subfigure} 
-    \caption{We hypothesize that R-spots is the result of ordered tail packing.
-	  Defining the membrane plane to be 0\degree, we measured the angles between each
-	  alkane chain tail centroid and its nearest neighbor centroids for the
-	  equilibrated sandwiched configuration simulated at 280K. Peaks
-	  that appear in each distribution are centered near $\pm~33\degree$. We radially
-	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
-	  configuration within the region bounding R-alkanes.
-	  Peaks appear in the same location as the angle distributions which corroborates
-	  our hypothesis.}~\label{fig:tail_packing}
+  \caption{(a) R-spots increases in intensity when the temperature of the system is 
+      lowered to 280K. (b) To isolate the main cause of R-spots, we removed all atoms
+      from the trajectory except for carbon atoms that constitute the tails. (c) The
+      simulated XRD pattern of the tails-only trajectory still shows R-spots. 
+      (d) We measured the average angle made between each monomer alkane tail and
+      the membrane plane. The average tilt angle (dashed line) is near -2\degree~which
+      is far from the 37\degree~tilt angle previously used to explain R-spots. 
+      (e) We hypothesize that R-spots is the result of ordered tail packing. Defining
+      the membrane plane to be 0\degree, we measured the angles between each alkane 
+      chain tail centroid and its nearest neighbor centroids for the equilibrated 
+      sandwiched configuration simulated at 280K. Peaks that appear in each distribution
+      are centered near $\pm~33\degree$. (f) We radially integrated the simulated XRD
+      patterns of the parallel displaced and sandwiched configuration within the region
+      bounding R-alkanes. Peaks appear in the same location as the angle distributions
+      which corroborates our hypothesis.}~\label{fig:tail_packing}
   \end{figure}
-
-%BJC: not sure if this figure is necessary.  
-%MRS6: kind of confusing with just the circles and no molecules to hang them on.
-%  \begin{figure}
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{hexagonal_tails_alt2.png} 
-%	%BJC: I can give the circle some depth if that makes it clearer
-%	\caption{Monomer tails prefer to pack in a hexagonal array. Each circle
-%		represents a monomer tail as seen if viewed by looking from the end of the tail
-%		to the pore center. Each color represents distinct monomers from adjacent
-%		layers.}~\label{fig:hex_tails}
-%  \end{figure}
 

### 2018-06-14 Ben_Manuscripts/structure_paper/supporting_information.tex
Draft updates + PMF stuff
edits

@@
 \documentclass[journal=jpcbfk,manusciprt=article]{achemso}
+
 \usepackage{graphicx}
@@
 \usepackage{subcaption}
+\usepackage{amsmath} 
 %\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
@@
 
-  \bibliographystyle{ieeetr}
+%  \bibliographystyle{ieeetr}
   \graphicspath{{./figures/}}  % put all the figures here
@@
 
+  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.
+
+  \section{Number of monomers per column}\label{section:monomers_per_column}
+
+  We chose to build all systems using 20 monomers per column. We made this choice
+  by considering a number of factors that directly affect the quality of our results. 
+  Clearly, choosing a small number of layers will cause the system to suffer from 
+  finite size effects. Even in our 20 monomer-per-column system, axial correlations
+  between stacked monomers persist throughout the entire correlation function (See
+  Figure ~\ref{M-fig:correlation}). The correlation function of the system which we
+  built with 40 monomers per column continues to oscillate for its full length
+  (Figure~\ref{fig:tall_correlation_full}). If we continue adding monomers, the 
+  correlation function will eventually fully decay but it is not worth the 
+  computational expense. Regardless, the correlation lengths calculated from 20
+  monomer per column simulations are in sufficient agreement with experiment.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{tall_correlation_full.png}
+  \caption{Oscillations persist throughout the length of the correlation 
+  function for the sandwiched system in the ordered basin built with 40 monomers
+  per column. The full system is ca. 17 nm tall so the full correlation function
+  covers half this length since periodicity forces the remaining length to be its
+  mirror image.}\label{fig:tall_correlation_full}
+  \end{figure}
+
+  We may be able to simulate systems using less than 20 monomers per column, but chose
+  to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
+  patterns. The size of the fourier space bin in each dimension is determined by 
+  $dfrac{2\pi}{L}$ where L is the length of a given box vector. The z-box vector 
+  for 20 monomer-per-column systems is $\approx$ 85 \AA which means we will see 
+  a reciprocal space resolution of 0.074 \AA$^{-1}$ in the z direction. Further decreasing
+  the resolution would increase the noise in the simulated patterns and make it more
+  difficult to measure the intensity of reflections of interest.
+
+  \section{Initial Configuration Dependence}\label{section:initial_config_dependence}
+%  \begingroup
+%	\fontsize{14pt}{12pt}\selectfont
+%	\textbf{Initial Configuration Dependence}
+%  \endgroup
+
+  \vspace{1em}
+  We addressed any major dependence on initial configuration in the main text.
+  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
+  monomers per layer. We also showed that systems are stable when monomer head
+  groups are oriented in the parallel displaced and sandwiched configurations
+  (See Figure~\ref{fig:stacking}). Our model is most consistent with experiment
+  when built with 5 monomers per layer, with layers stacked 3.7 \AA~apart in 
+  the parallel displaced configuration.
+
+  There are three other parameters whose choice may influence the equilibrium
+  structure: initial pore spacing, initial pore radius and initial distance
+  between layers. Here we show the results of a sensitivity analysis performed
+  on the three parameters. To reduce the size of the sensitivity analysis, we
+  only tested systems built with 5 monomers per layer with layers stacked in 
+  the parallel displaced configuration. We equilibrated all systems according
+  to the dry equilibration procedure.
+
+  %\begin{enumerate}
+
+  %	  \item \underline{Initial pore spacing}
+  \subsection{Initial pore spacing}\label{section:initial_pore_spacing}
+
+	  We tested five different initial pore spacings, defined as the
+	  distance between the central axis of each pore with all others
+	  (Figure~\ref{fig:p2p_diagram}). To reduce the number of variables, we held the
+	  pore radius constant, at 6 \AA~and the distance between layers at 3.7 \AA~since
+	  those were the values used in our optimal system in the main text. We
+	  prioritized ensuring that resulting configurations maintain the expected
+	  hexagonal symmetry. If initial pore spacing is too small, we observe repulsion
+	  between columns which disrupts equilibration. If the pore spacing is too large
+	  the pores squeeze together, but in a distorted hexagonal array because the xy
+	  initial translation of the pores is somewhat erratic.
+
+%	  If the initial pore spacing is chosen to be
+%	  too small, pore columns abruptly repel each other as soon as they are able to
+%	  overcome the restraining potential present as part of the dry equilibration
+%	  procedure. We avoided using systems that exhibit this behavior since the
+%	  behavior increases the chances of a system to become kinetically trapped in an
+%	  undesired metastable free energy basin.
+
+	  \begin{enumerate}
+
+		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
+		have a test system with an intial spacing below the experimental value. As soon
+		as the restraining potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the
+		columns are able to repel resulting in a large jump in pore spacing
+		(Figure~\ref{fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
+%		There is a large uncertainty in this value because the 1-4 pore spacing
+%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
+%		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
+%		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
+%                towards cubic packing.
+
+		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
+		it closely matches the experimental pore spacing. Again, we observe abrupt
+		repulsion of columns once the restraining potential is switched to 56 KJ
+		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
+%		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
+%		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
+%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
+%		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
+%		spacings is 3.96 nm.
+
+		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
+		than the experimental value. This systems exhibits the smallest response to our 
+ 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
+        value for all our simulations in the main text.
+        %The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
+		%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
+		%pore spacing. We chose to use this value for all our simulations in the main
+		%text.
+
+		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \%
+		larger than the experimental value. Once the restraining potential reaches 56
+		KJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
+		a linear trend (Figure~\ref{fig:p2p_50}).
+%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
+%		There is a large
+ %               uncertainty with this value because, again, the array of pores deviates from 
+ %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
+  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
+   %             response.
+
+		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
+		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
+		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
+		changes erratically until it begins to settle when the force constants are
+		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
+		avoiding a system such as this where vacuum gaps between pore columns are
+		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
+%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
+ %               spacing of 3.99 \AA~ which distorts the hexagonal array.
+
+	  \end{enumerate}
+
+	  \begin{figure}[!htb]
+		\centering
+		\includegraphics[width=0.4\textwidth]{p2p_diagram.png}
+		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
+		equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
+		are the same.}~\label{fig:p2p_diagram}
+	  \end{figure}
+
+	  %BJC: Could put vertical lines to indicate where position restraint values are reduced
+  	  \begin{figure}[!htb]
+		\centering
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_39.png}\quad
+			\vspace{-1.25em}
+			\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
+		\end{subfigure}
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_41.png}\quad
+			\vspace{-1.25em}
+			\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
+		\end{subfigure}
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_45.png}
+			\vspace{-1.25em}
+			\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
+		\end{subfigure}
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_50.png}\quad	
+			\vspace{-1.25em}
+			\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
+		\end{subfigure}
+		\begin{subfigure}{0.3\textwidth}
+			\includegraphics[width=\textwidth]{p2p_55.png}
+			\vspace{-1.25em}
+			\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
+		\end{subfigure}
+
+		\caption{The pore spacing during the restrained portion of the
+			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
+			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 KJ
+			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
+			experimental value (a) or at the experimental value (b), there is an abrupt
+			change in pore spacing when the position restraints are reduced to 56 KJ
+			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA~apart (c) the pore spacing
+			remains relatively stable. When pores are spaced 50 \AA~apart (d), the pore
+			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
+			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA~apart (e), so that monomers
+			do not intersect with adjacent pores, and position restraints are reduced to 56
+			KJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
+			when force constants are reduced below 3 KJ mol$^{-1}$ nm$^{-2}$.} 
+		\label{fig:p2p}
+	  \end{figure}
+
+%	  \item \underline{Initial pore radius}
+	  \subsection{Initial pore radius}\label{section:initial_pore_radius}
+
+	  We tested 3 different pore radii, defined as shown in
+	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
+	  pore spacing constant at 45 \AA~and the initial distance between layers
+	  constant at 3.7 \AA. Equilibrated values of pore radii are presented in
+	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
+	  as the average distance of all carbonyl carbons (See
+	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
+	  Statistics for the pore radii reported were generated from the timeseries
+	  representing the average pore radius at each frame. We detected equilibration
+	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
+	  and standard deviation of pore radii using only data points collected after
+	  equilibration was detected.
+
+	  \begin{enumerate}
+
+		\item 2.5 \AA~: The smallest pore radius that we can achieve
+		before energy minimization becomes problematic is 2.5 \AA. After being run
+		through the full dry equilibration procedure, the average pore radius is 0.40
+		$\pm$ 0.01 \AA.
+
+		\item 5 \AA~: We tested a pore radius of 5 \AA~because it is
+		slightly larger than the equilibrated pore radius of the system simulated with
+		an intial pore radius of 2.5 \AA. After being run through the full dry
+		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
+		agrees with the 2.5 \AA~configuration within uncertainty.
+
+		\item 8 \AA~: The largest pore radius that can achieved before
+		energy minimization becomes problematic is 8 \AA. One should use caution with
+		such a structure because of the relatively large vacuum space that is created
+		in the pore region of the initial configuration. After being run through the
+		full dry equilibration procedure, we see a combination of cylindrical and
+		slit-like pores (Figure~\ref{fig:slits}). Measuring the pore radius of this
+		system does not have a concrete meaning since slits do not have a single
+		radius, but its calculated value is reported in Table ~\ref{table:radii}. We
+		are wary of such a non-symmetric structure and choose not to use a pore radius
+		of 8 \AA~for our starting configurations.
+
+	  \end{enumerate}
+
+	  \begin{table}[h]
+	  \centering
+	  \begin{tabular}{cc}
+	  \toprule
+	  Initial Pore Radius & Equilibrated Pore Radius \\
+	  \midrule
+	  % BJC: to be updated once simulations are run out long enough
+	  2.5 \AA & $0.40 \pm 0.01$ \AA \\
+	  5 \AA   & $0.42 \pm 0.01$ \AA \\ % final result
+	  8 \AA   & $0.69 \pm 0.01$ \AA \\
+	  \bottomrule
+	  \end{tabular}
+	  \caption{The average pore radii of systems built with an initial pore
+		  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
+		  the pore radius is too large, slit pores may form.}~\label{table:radii}
+	  \end{table}
+
+	  \begin{figure}[!htb]
+	  \centering
+          \includegraphics[width=\textwidth]{slit_pores.png}
+	  \caption{A system that was built with an initial pore radius of 8
+		  \AA~equilibrates to a structure that exhibits both cylindrical and slit-like
+		  pores. As pictured here, sodium ions are colored blue, carbon atoms in the
+		  aromatic ring of the head group are colored orange and all else is colored
+		  cyan.}~\label{fig:slits}
+	  \end{figure}
+
+%	  \item \underline{Initial distance between layers}
+	  \subsection{Initial distance between layers}\label{section:initial_dbwl}
+
+	  We tested 3 different initial layer spacings, defined as the distance
+	  between the planes of aromatic rings in each layer. Systems built with layers
+	  stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
+	  also tested a system built with layers stacked 10 \AA~ apart.
+
+	  Figure~\ref{fig:dbwl_10} shows the structure of an assembly built
+	  with an initial layer spacing of 10 \AA~immediately after the restrained
+	  portion of the equilibration procedure. Since we used position restraints, the
+	  simulations were run in the NVT ensemble. When layer spacing is large, such as
+	  this situation, there is a significant amount of vacuum space which the monomer
+	  attempts to fill. Even if turning pressure control on allows the system to
+	  recover the geometry of the hexagonal phase, we would likely need much longer
+	  equilibration times, and it will almost certainly get trapped in a metastable
+	  configuration that bears no resemblence to the experimental profile.
+
+	  \begin{figure}[!htb]
+		\centering
+		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
+		\caption{When layers are initially stacked 10 \AA~apart and the system
+                is equilibrated using the dry equlibration procedure, large vacuum gaps
+		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
+	  \end{figure}
+
+%  \end{enumerate}
+
+%  \noindent
+%  \begingroup
+%        \fontsize{14pt}{14pt}\selectfont
+%	\textbf{Calculation of pore-to-pore spacing statistics}
+%  \endgroup
+
+  \begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
+	\caption{There are five pore-to-pore distances that are equal in a perfect
+		hexagon. If each number in the diagram represents the center of a
+		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
+		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
+		are independent. For example, the distance from 1 to 4 is defined by
+		the location of all other pore centers.}
+	\label{fig:p2p_diagram}
+  \end{figure}
+
+  \section{Equilibration Details}\label{section:equilibration}
+
+  We developed equilibration schemes to create dry and wet configurations. Both
+  schemes start with an initial configuration generated according to the previous
+  guidelines. To create a dry configuration, we fix monomer head groups in the
+  sandwiched or parallel-displaced configuration using position restraints with a
+  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in
+  the NVT ensemble which allows the monomer tails to settle without disrupting
+  the ordering of the head groups. Doing so also mitigates system dependence on
+  initial monomer configuration. Every 50 ps, we reduce the force constants by
+  the square root of its previous value. Once the force constant is below 10 KJ
+  mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
+  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
+  unrestrained structure to equilibrate for 5 ns in the NPT ensemble
+  with pressure controlled by the berendsen barostat. Next, we run long NPT
+  equilibration simulations for at least 400 ns using the Parrinello-Rahman
+  barostat with a time constant of 10 ps.
+
+  % MRS6: some parameters missing here (time run between insertions, etc). 
+  % I assume they are in supporting information?
+  % BJC5: all water is present in initial configuration. This did not follow the more
+  % complex procedures that I've come up with since then. 
+  In order to create a ``wet'' system, we solvated an initial configuration with
+  water using \texttt{gmx solvate}. We remove all water molecules placed outside
+  the pore region. Then we randomly remove water molecules inside the pore region
+  until the pores reach the desired concentration of water. The remainder of the
+  equilibration follows the same procedure as the dry system.
+
   \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
@@
 
-  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.
-
-  \section{Initial Configuration Dependence}\label{section:initial_config_dependence}
-%  \begingroup
-%	\fontsize{14pt}{12pt}\selectfont
-%	\textbf{Initial Configuration Dependence}
-%  \endgroup
-
-  \vspace{1em}
-  We addressed any major dependence on initial configuration in the main text.
-  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
-  monomers per layer. We also showed that systems are stable when monomer head
-  groups are oriented in the parallel displaced and sandwiched configurations
-  (See Figure~\ref{fig:stacking}). Our model is most consistent with experiment
-  when built with 5 monomers per layer, with layers stacked 3.7 \AA~apart in 
-  the parallel displaced configuration.
-
-  There are three other parameters whose choice may influence the equilibrium
-  structure: initial pore spacing, initial pore radius and initial distance
-  between layers. Here we show the results of a sensitivity analysis performed
-  on the three parameters. To reduce the size of the sensitivity analysis, we
-  only tested systems built with 5 monomers per layer with layers stacked in 
-  the parallel displaced configuration. We equilibrated all systems according
-  to the dry equilibration procedure.
-
-  %\begin{enumerate}
-
-  %	  \item \underline{Initial pore spacing}
-  \subsection{Initial pore spacing}\label{section:initial_pore_spacing}
-
-	  We tested five different initial pore spacings, defined as the
-	  distance between the central axis of each pore with all others
-	  (Figure~\ref{fig:p2p_diagram}). To reduce the number of variables, we held the
-	  pore radius constant, at 6 \AA~and the distance between layers at 3.7 \AA~since
-	  those were the values used in our optimal system in the main text. We
-	  prioritized ensuring that resulting configurations maintain the expected
-	  hexagonal symmetry. If initial pore spacing is too small, we observe repulsion
-	  between columns which disrupts equilibration. If the pore spacing is too large
-	  the pores squeeze together, but in a distorted hexagonal array because the xy
-	  initial translation of the pores is somewhat erratic.
-
-%	  If the initial pore spacing is chosen to be
-%	  too small, pore columns abruptly repel each other as soon as they are able to
-%	  overcome the restraining potential present as part of the dry equilibration
-%	  procedure. We avoided using systems that exhibit this behavior since the
-%	  behavior increases the chances of a system to become kinetically trapped in an
-%	  undesired metastable free energy basin.
-
-	  \begin{enumerate}
-
-		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
-		have a test system with an intial spacing below the experimental value. As soon
-		as the restraining potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the
-		columns are able to repel resulting in a large jump in pore spacing
-		(Figure~\ref{fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
-%		There is a large uncertainty in this value because the 1-4 pore spacing
-%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
-%		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
-%		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
-%                towards cubic packing.
-
-		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
-		it closely matches the experimental pore spacing. Again, we observe abrupt
-		repulsion of columns once the restraining potential is switched to 56 KJ
-		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
-%		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
-%		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
-%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
-%		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
-%		spacings is 3.96 nm.
-
-		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
-		than the experimental value. This systems exhibits the smallest response to our 
- 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
-        value for all our simulations in the main text.
-        %The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
-		%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
-		%pore spacing. We chose to use this value for all our simulations in the main
-		%text.
-
-		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \%
-		larger than the experimental value. Once the restraining potential reaches 56
-		KJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
-		a linear trend (Figure~\ref{fig:p2p_50}).
-%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
-%		There is a large
- %               uncertainty with this value because, again, the array of pores deviates from 
- %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
-  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
-   %             response.
-
-		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
-		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
-		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
-		changes erratically until it begins to settle when the force constants are
-		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
-		avoiding a system such as this where vacuum gaps between pore columns are
-		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
-%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
- %               spacing of 3.99 \AA~ which distorts the hexagonal array.
-
-	  \end{enumerate}
-
-	  \begin{figure}[!htb]
-		\centering
-		\includegraphics[width=0.4\textwidth]{p2p_diagram.png}
-		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
-		equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
-		are the same.}~\label{fig:p2p_diagram}
-	  \end{figure}
-
-	  %BJC: Could put vertical lines to indicate where position restraint values are reduced
-  	  \begin{figure}[!htb]
-		\centering
-		\begin{subfigure}{0.3\textwidth}
-			\includegraphics[width=\textwidth]{p2p_39.png}\quad
-			\vspace{-1.25em}
-			\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
-		\end{subfigure}
-		\begin{subfigure}{0.3\textwidth}
-			\includegraphics[width=\textwidth]{p2p_41.png}\quad
-			\vspace{-1.25em}
-			\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
-		\end{subfigure}
-		\begin{subfigure}{0.3\textwidth}
-			\includegraphics[width=\textwidth]{p2p_45.png}
-			\vspace{-1.25em}
-			\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
-		\end{subfigure}
-		\begin{subfigure}{0.3\textwidth}
-			\includegraphics[width=\textwidth]{p2p_50.png}\quad	
-			\vspace{-1.25em}
-			\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
-		\end{subfigure}
-		\begin{subfigure}{0.3\textwidth}
-			\includegraphics[width=\textwidth]{p2p_55.png}
-			\vspace{-1.25em}
-			\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
-		\end{subfigure}
-
-		\caption{The pore spacing during the restrained portion of the
-			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
-			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 KJ
-			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
-			experimental value (a) or at the experimental value (b), there is an abrupt
-			change in pore spacing when the position restraints are reduced to 56 KJ
-			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA~apart (c) the pore spacing
-			remains relatively stable. When pores are spaced 50 \AA~apart (d), the pore
-			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
-			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA~apart (e), so that monomers
-			do not intersect with adjacent pores, and position restraints are reduced to 56
-			KJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
-			when force constants are reduced below 3 KJ mol$^{-1}$ nm$^{-2}$.} 
-		\label{fig:p2p}
-	  \end{figure}
-
-%	  \item \underline{Initial pore radius}
-	  \subsection{Initial pore radius}\label{section:initial_pore_radius}
-
-	  We tested 3 different pore radii, defined as shown in
-	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
-	  pore spacing constant at 45 \AA~and the initial distance between layers
-	  constant at 3.7 \AA. Equilibrated values of pore radii are presented in
-	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
-	  as the average distance of all carbonyl carbons (See
-	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
-	  Statistics for the pore radii reported were generated from the timeseries
-	  representing the average pore radius at each frame. We detected equilibration
-	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
-	  and standard deviation of pore radii using only data points collected after
-	  equilibration was detected.
-
-	  \begin{enumerate}
-
-		\item 2.5 \AA~: The smallest pore radius that we can achieve
-		before energy minimization becomes problematic is 2.5 \AA. After being run
-		through the full dry equilibration procedure, the average pore radius is 0.40
-		$\pm$ 0.01 \AA.
-
-		\item 5 \AA~: We tested a pore radius of 5 \AA~because it is
-		slightly larger than the equilibrated pore radius of the system simulated with
-		an intial pore radius of 2.5 \AA. After being run through the full dry
-		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
-		agrees with the 2.5 \AA~configuration within uncertainty.
-
-		\item 8 \AA~: The largest pore radius that can achieved before
-		energy minimization becomes problematic is 8 \AA. One should use caution with
-		such a structure because of the relatively large vacuum space that is created
-		in the pore region of the initial configuration. After being run through the
-		full dry equilibration procedure, we see a combination of cylindrical and
-		slit-like pores (Figure~\ref{fig:slits}). Measuring the pore radius of this
-		system does not have a concrete meaning since slits do not have a single
-		radius, but its calculated value is reported in Table ~\ref{table:radii}. We
-		are wary of such a non-symmetric structure and choose not to use a pore radius
-		of 8 \AA~for our starting configurations.
-
-	  \end{enumerate}
-
-	  \begin{table}[h]
-	  \centering
-	  \begin{tabular}{cc}
-	  \toprule
-	  Initial Pore Radius & Equilibrated Pore Radius \\
-	  \midrule
-	  % BJC: to be updated once simulations are run out long enough
-	  2.5 \AA & $0.40 \pm 0.01$ \AA \\
-	  5 \AA   & $0.42 \pm 0.01$ \AA \\ % final result
-	  8 \AA   & $0.69 \pm 0.01$ \AA \\
-	  \bottomrule
-	  \end{tabular}
-	  \caption{The average pore radii of systems built with an initial pore
-		  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
-		  the pore radius is too large, slit pores may form.}~\label{table:radii}
-	  \end{table}
-
-	  \begin{figure}[!htb]
-	  \centering
-          \includegraphics[width=\textwidth]{slit_pores.png}
-	  \caption{A system that was built with an initial pore radius of 8
-		  \AA~equilibrates to a structure that exhibits both cylindrical and slit-like
-		  pores. As pictured here, sodium ions are colored blue, carbon atoms in the
-		  aromatic ring of the head group are colored orange and all else is colored
-		  cyan.}~\label{fig:slits}
-	  \end{figure}
-
-%	  \item \underline{Initial distance between layers}
-	  \subsection{Initial distance between layers}\label{section:initial_dbwl}
-
-	  We tested 3 different initial layer spacings, defined as the distance
-	  between the planes of aromatic rings in each layer. Systems built with layers
-	  stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
-	  also tested a system built with layers stacked 10 \AA~ apart.
-
-	  Figure~\ref{fig:dbwl_10} shows the structure of an assembly built
-	  with an initial layer spacing of 10 \AA~immediately after the restrained
-	  portion of the equilibration procedure. Since we used position restraints, the
-	  simulations were run in the NVT ensemble. When layer spacing is large, such as
-	  this situation, there is a significant amount of vacuum space which the monomer
-	  attempts to fill. Even if turning pressure control on allows the system to
-	  recover the geometry of the hexagonal phase, we would likely need much longer
-	  equilibration times, and it will almost certainly get trapped in a metastable
-	  configuration that bears no resemblence to the experimental profile.
-
-	  \begin{figure}[!htb]
-		\centering
-		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
-		\caption{When layers are initially stacked 10 \AA~apart and the system
-                is equilibrated using the dry equlibration procedure, large vacuum gaps
-		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
-	  \end{figure}
-
-%  \end{enumerate}
-
-%  \noindent
-%  \begingroup
-%        \fontsize{14pt}{14pt}\selectfont
-%	\textbf{Calculation of pore-to-pore spacing statistics}
-%  \endgroup
-
-  \begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
-	\caption{There are five pore-to-pore distances that are equal in a perfect
-		hexagon. If each number in the diagram represents the center of a
-		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
-		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
-		are independent. For example, the distance from 1 to 4 is defined by
-		the location of all other pore centers.}
-	\label{fig:p2p_diagram}
-  \end{figure}
-
   \section{The nematic order parameter}\label{method:nematic_order}
@@
 
+  \section{Solvation}\label{section:solvation}
+
+  % formatting taken from : https://tex.stackexchange.com/questions/239715/add-titles-for-rows-and-columns-in-a-subfloat
+  \newlength{\tempdima}
+  \newcommand{\rowname}[1]% #1 = text
+  {\rotatebox{90}{\makebox[\tempdima][c]{\textbf{#1}}}}
+
+  \renewcommand{\thesubfigure}{\alph{subfigure}}
+  \newcommand{\mycaption}[1]% #1 = caption
+  {\refstepcounter{subfigure}\textbf{(\thesubfigure) }{\ignorespaces #1}}
+
+  \begin{figure}[!htb]
+  \begin{subfigure}{0.915\textwidth}
+  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
+  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
+  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
+  	\rowname{Parallel Displaced}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_5.png}\\[-1ex]
+  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
+  	\rowname{Sandwiched}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_1.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
+  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_5.png}\\[-1ex]
+  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
+  	\end{tabular}
+  \end{subfigure}
+  \begin{subfigure}{0.075\textwidth}
+  	\includegraphics[width=\textwidth]{colorbar_jet.png}
+  \end{subfigure}
+	\caption{Adding 1 wt \% water to the ordered basin dry systems causes an increase in the intensity
+	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
+	of water increase discrepancies with experiment} %MRS7:by increasing disorder?
+  \label{fig:solvation}
+
+  \end{figure}
+
   \section{Crosslinking algorithm details}\label{section:xlink}
@@
   Crosslinking of the the monomer Na-GA3C11 occurs by a UV initiated free
-  radical polymerization (Figure~\ref{fig:xlink_mech}).  Head-to-tail addition
+  radical polymerization (FRP) (Figure~\ref{fig:xlink_mech}). Head-to-tail addition
   takes place between terminal vinyl groups on each of the monomer tails. We
@@
 	  crosslinking.}\label{fig:xlink_mech}
+  \end{figure}
+
+  We based our cross-linking algorithm on the known reaction mechanism.
+  FRPs require an initiator which bonds to the system, meaning new atoms are
+  introduced into the system. For simplicity, we simulated the initiator as
+  hydrogen and made it present in the simulation by including them as dummy atoms
+  in all possible locations where an addition could occur. We carry out the
+  cross-linking procedure iteratively. During each iteration, the algorithm
+  selects eligible bonding carbon atoms based on a distance cut-off. The algorithm
+  then updates the topology with new bonds and changes dummy hydrogen atoms to appropriate
+  hydrogen atom types. We only considered head-to-tail addition
+  due to its dominance in the real system \cite{young_introduction_2011}. We did
+  not consider direction of attack because the resultant mixture is racemic.
+
+  Our implementation requires long simulation times to achieve high cross-link 
+  densities. A typical cross-linking procedure can take up to 24 hours. In
+  order to collect equilibrated data, further NPT simulation is necessary. We
+  typically run a cross-linked system for an additional 100 ns to allow the system
+  to readjust. For those reasons we did not cross-link all systems tested.
+
+  \section{Ionic Conductivity}\label{section:ionic_conductivity}
+
+  In the main text, we calculated ionic conductivity using the Nernst Einstein 
+  relationship. We also measured ionic conductivity using a second method, 
+  termed the Collective Diffusion model, for robustness. The collective 
+  diffusion model measures the movement of the collective variable, Q, which
+  is defined as the amount of charge transfer through the system and can be 
+  thought to represent the center of charge of the system. The conductance, 
+  $\gamma$, of the system can be calculated as:
+  \begin{equation}
+	 \gamma = \dfrac{D_Q}{k_b T} 
+	\label{eqn:collective_diffusion}
+  \end{equation}
+  $D_Q$ is the diffusion coefficient of the collective variable Q and is 
+  calculated using the Einstein relation. We convert the resulting value
+  to ionic conductivity by multiplying by channel length and dividing by
+  the membrane cross sectional area. One can access a detailed derivation of 
+  the model elsewhere\cite{liu_collective_2013}.
+
+  \begin{figure}[!htb]
+        \centering
+        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
+        \caption{The Collective Diffusion model and the nernst-einstein relation yield
+        agreeing values of ionic conductivity for both types of ordered basin systems 
+        simulated. Both methods estimate the value of the ionic conductivity to be an 
+        order of magnitude higher than the experimental value. There is more noise in
+        the collective diffusion model because there is inherently less data that 
+        can be used for its calculation. For that reason, we use only the Nernst 
+        Einstein relationship in the main text.}
+        \label{fig:conductivity}
   \end{figure}
@@
 
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{width=0.45\textwidth}
+%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
+%  \caption{}\label{fig:rdouble_offset_solvated_rzplot}
+%  \end{subfigure}
+%  \begin{subfigure}{width=0.45\textwidth}
+%  \includegraphics[width=\textwidth]{rzplot_pore1_removed.png}
+%  \caption{}\label{fig:rzplot_pore1_removed}
+%  \end{subfigure}
+%  \caption{(a) The simulated diffraction pattern of a system simulated in an ordered basin 
+%  parallel displaced configuration with 1 wt\% water shows R-double at $mathbf{q}=(0, 0.7) \AA^{-1}$.
+%  (b) When we remove }\label{fig:pore1_removed}
+%  \end{figure}
+
 \clearpage

### 2018-06-14 HII/Scripts/regional_density.py

@@ -119,7 +119,7 @@ if __name__ == "__main__":
                              label=names[j])
             # plt.title(regions[i], fontsize=14)
             plt.legend(fontsize=11)
-            plt.ylabel('Component Number Density (number/nm$^2$)', fontsize=14)
+            plt.ylabel('Component Number Density (number/nm$^3$)', fontsize=14)
             plt.xlabel('Distance from pore center, r (nm)', fontsize=14)
             plt.axes().tick_params(labelsize=14)
             # plt.ylim([0, 0.6])

### 2018-06-15 Ben_Manuscripts/structure_paper/Draft.tex
Edits

@@
   Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
-  liquid crystalline domains, formed when Na-GA3C11 monomers self-assemble, are
+  liquid crystalline domains, formed when monomers self-assemble, are
   isotropically aligned which is detrimental to membrane permeability.
@@
   whose geometry does not require alignment. In 2014, Feng et al.~showed that one
-  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
-  subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
-  In 2016, Feng et al. showed that one could obtain the same result using a second
-  technique termed soft confinement\cite{feng_thin_2016}. Current experimental 
-  efforts are focused on extending the method to the H\textsubscript{II} phase 
-  and characterizing the performance of these newly aligned systems.
+  can align Col\textsubscript{h} hexagonal domains, created by the monomer Na-GA3C11,
+  using a magnetic field with subsequent cross-linking to lock the structure in 
+  place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
+  the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
+  Current experimental efforts are focused on extending the method to the 
+  H\textsubscript{II} phase and characterizing the performance of these newly aligned systems.
 
@@
   formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-  phase is a simpler starting point. The system has no water which will allow us
+  phase is a simpler starting point. The system has no water which allowed us
   to simulate longer timescales, and there exists detailed experimental
@@
 	\item \textit{R-double}: A weak intensity line, located at exactly half
-	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
-	space periodic spacing of 7.4 \AA~. Since this reflection corresponds to double
+	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to real
+	space periodicity of 7.4 \AA. Since this reflection corresponds to double
 	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
@@
 	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
-	relative intensity.  Accordingly, we name these reflection R-spots. The
+	relative intensity.  Accordingly, we name these reflections R-spots. The
 	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
@@
  	In the system we are studying, there are long-range 2D correlations in the 
- 	hexagonal array of pores (xy plane) and short range correlations in the z-direction.
-    %MRS7: look carefully at tenses.  Don't describe the research in future tense. 
-    % if it's describing your presentation of the research in the paper , use present tense. 
-    % If it's describing something you did, use past tense. I changed some of them, but not all.
- 	%We will use 
-    In this study, we use our atomistic molecular model to study how the system's structure is 
-    affected by the density of monomers surrounding each pore's hydrophilic core.
+ 	hexagonal array of pores (xy plane) and short range z-direction correlations between 
+        stacked columns of monomers. In this study, we use our atomistic molecular model
+        to study how the system's structure is affected by the density of these monomer columns
+        that surround each pore's hydrophilic core.
 
@@
 
+        \item Is it necessary to include any water in order to appropriately model the 
+        Col\textsubscript{h} phase? \label{point:water}
+
+	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
+	ambient water are leached into the system. The hydrogen bonding network formed by the 
+	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
+	to see if there is any meaningful structural difference between a "dry" and a "wet" system.
+
 	\item What is the chemical composition of the pores?\label{point:composition}
@@
 	of the pores, the partition between the hydrophilic and hydrophobic regions, and its 
-	sensitivity to initial configuration.
-
-    \item Is it necessary to include any water in order to appropriately model the 
-    Col\textsubscript{h} phase? \label{point:water}
-
-	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
-	ambient water may be leached into the system. The hydrogen bonding network formed by the 
-	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
-	to see if there is any meaningful structural difference between a "dry" and "wet" system.
+	sensitivity to initial configuration, including both dry and wet systems.
 
@@
   longer timescales. Ultimately, we chose to build a system with 20 monomers
-  per column in order to obtain sufficient resolution when simulating
-  X-ray diffraction patterns (see further discussion in section S\ref{S-section:monomers_per_column}).
-  %MRS7: refer to supporting information (if it's there) for more discussion on stability as a function of height?
-  %BJC6: gave it a shot in supplemental
+  per column in order to minimize finite size effects with reasonable computational expense 
+  and to obtain sufficient resolution when simulating XRD patterns (see further discussion
+  in section S\ref{S-section:monomers_per_column}).
 
@@
   Supporting information, section S\ref{S-section:initial_config_dependence}. The 
-  distance between vertically stacked monomers, the position of monomers with respect 
+  distance between vertically stacked monomers, the xy position of monomers with respect 
   to vertically adjacent monomers, and the number of columns per pore do influence the 
@@
   We chose the vertical spacing between monomers for the initial configuration based
-  on R-$\pi$ and then allowed the system to readjust during equilibration. Each monomer was
-  rotated so the plane of its aromatic head group would be coplanar with the xy plane. We
+  on R-$\pi$ and then allowed the system to readjust during equilibration. We rotated 
+  each monomer so the plane of its aromatic head group would be coplanar with the xy plane. We
   explored three different initial monomer spacings. The first is exactly
@@
   schemes start with an initial configuration generated according to the previous
-  guidelines. For wet systems, the desired concentration of water was added to 
-  the initial configuration and we carried out equilibration in the same way
+  guidelines. For wet systems, we added the desired concentration of water to 
+  the initial configuration and carried out equilibration in the same way
   as the dry systems. First, we fixed monomer head groups in place using position
@@
   released the position restraints by decreasing the force constants over a series
-  of simulations. We allowed the resulting unrestrained structure to equilibrate for
+  of NVT simulations. We allowed the resulting unrestrained structure to equilibrate for
   5 ns in the NPT ensemble with pressure controlled by the berendsen barostat 
@@
   of L as the square root of the diagonal entry of the covariance matrix of 
-  optimized fit parameters.
+  optimized fit parameters.  %BJC6: reference scipy curve_fit?
 
@@
   carbon atoms making up the monomer tails. We binned the radial distance of all
-  atoms in each group from the pore centers, then normalized by the area of the
+  atoms in each group from the pore centers, then normalized by the volume of the
   annulus defined by the bin edges and the z box vector (See Figure~S\ref{S-fig:rdf_diagram}).
@@
   patterns differ from experiment in those regions in all cases. Specifically, in contrast
-  to the experimental WAXS pattern, R-$\pi$ as it appears the simulated diffraction 
-  patterns intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set
+  to the experimental WAXS pattern, R-$\pi$, as it appears in the simulated diffraction 
+  patterns, intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set
   an upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$. 
@@
   consistent with the experimental value of 4.12 nm derived from SAXS measurements 
-  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
-  systems built with 5 columns per pore. Ordered basin systems built with 6 columns per pore,
-  have an equilibrated pore spacing ca. 0.50 nm higher than experiment. Ordered basin systems
-  built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower than experiment.
-
-  %BJC5: thesis needs rewording.
-  Monomers in disordered basin systems built with 6 columns-per-pore stack too far apart.
-  Those in the disordered sandwiched and disordered parallel displaced configurations stack 
-  $\approx$ 4.87 and 4.94~\AA apart respectively, which is ca. 1.2~\AA further apart than 
-  suggested by experiment. 5 column-per-pore systems stack, at a maximum, 0.9 ~\AA further
-  apart than experiment (see Table~\ref{table:correlation_length}). Methodology for calculating
-  equilibrium stacking distance is fully explained in section~\ref{section:rpi}.
+  (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4 columns per pore equilibrate
+  to an average pore spacing 0.25 nm lower than experiment. Ordered basin systems built with
+  6 columns per pore, have an equilibrated pore spacing ca. 0.50 nm higher than experiment.
+  Monomers in disordered basin systems built with 6 columns-per-pore agree with experiment 
+  within error, but stack too far apart. Those in the disordered sandwiched and disordered
+  parallel displaced configurations stack $\approx$ 4.87 and 4.94 \AA~apart respectively, 
+  which is ca. 1.2~\AA further apart than suggested by experiment. 5 column-per-pore systems
+  stack, at a maximum, 0.9 \AA~further apart than experiment (see Table~\ref{table:correlation_length}). 
+  The remainder of this discussion will focus on the analysis of systems built with 5 columns per pore.
+
+% BJC6: I don't think I need to say the following in above paragraph since its all in the methods.
+% Our methodology for calculating equilibrium stacking distance is fully explained in section~\ref{section:rpi}.
 
@@
   appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
-  maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
+  maximum at $q_z < 1.5~\AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
   rather than 3.7 \AA. R-double does not appear in any of the patterns.
@@
   The simulated XRD patterns of the parallel displaced configurations show an additional
-  reflection due to their helical structure. There are horizontal reflections near $|q_z|= 
+  reflection due to their helical structure. There are weak horizontal reflections near $|q_z|= 
   0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
@@
   R-$\pi$, since that is where it appears experimentally. The intensity of R-spots is slightly
-  lower than experiment in all cases. There is no R-double intensity to be measured. Figures
+  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
+  agrees with experiment. There is no R-double intensity to be measured. Figures
   are provided in section S\ref{S-section:xrd_intensities} to make these measurements clear.
@@
   There are clear differences between simulated and experimental results that must be addressed
-  and justified. We will explore the possible origin of each experimental reflection and form 
+  and justified. We will explore the possible origin of select experimental reflections and form 
   structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
@@
   able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the 
-  tails stay nearly flat, we plotted the centroids of the tails (Figure \ref{fig:centroids})
+  tails stay nearly flat, we plotted their centroids (Figure \ref{fig:centroids})
   and measured the angle between each centroid and its nearest neighbors with respect to the 
@@
   \caption{(a) R-spots increases in intensity when the temperature of the system is 
-      lowered to 280K. (b) To isolate the main cause of R-spots, we removed all atoms
-      from the trajectory except for carbon atoms that constitute the tails. (c) The
-      simulated XRD pattern of the tails-only trajectory still shows R-spots. 
-      (d) We measured the average angle made between each monomer alkane tail and
-      the membrane plane. The average tilt angle (dashed line) is near -2\degree~which
-      is far from the 37\degree~tilt angle previously used to explain R-spots. 
-      (e) We hypothesize that R-spots is the result of ordered tail packing. Defining
+      lowered to 280K. (b) We measured the average angle made between each monomer 
+      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
+      near -2\degree~which is far from the 37\degree~tilt angle previously used to
+      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
+      from the trajectory except for carbon atoms that constitute the tails. The
+      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
+      Since the tails stay relatively flat, we plotted the centroid of each tail 
+      and observed that they pack hexagonally (for example, green colored centroids
+      in the plot surround the red centroid in hexagonal fashion). (e) We hypothesize
+      that R-spots is the result of ordered tail packing. Defining
       the membrane plane to be 0\degree, we measured the angles between each alkane 
@@
   columns and the degree to which they are correlated. These metrics helped us disect the 
-  various contributions to R-$\pi$. Figure ~\ref{fig:correlation} shows $g(z)$ for all 
+  various contributions to R-$\pi$. Figure~\ref{fig:correlation} shows $g(z)$ for all 
   systems tested.
@@
   cases. This behavior is not surprising since GAFF models atoms as point charges and does not 
-  appropriately model the aromatic $\pi-\pi$ interactions which would cause the monomers to 
-  stack closer together. Additionally, it is possible that the tails prevent close stacking of
-  monomer head groups and we do not achieve the timescales necessary for them to rearrange into
-  a necessarily more tightly packed configuration. Ordered basin systems are likely the best 
-  choice for transport studies.
+  appropriately model the aromatic $\pi-\pi$ interactions which would make it more energetically
+  favorable for the monomers to stack closer together. Additionally, it is possible that the 
+  tails prevent close stacking of monomer head groups and we do not achieve the timescales 
+  necessary for them to rearrange into a necessarily more tightly packed configuration. Ordered
+  basin systems are likely the best choice for transport studies.
 
@@
   not extract a reliable correlation length from the disordered parallel displaced configuration
-  since the peaks do not show clear patterns that can easily be fit to exponential decay. The 
+  since the peaks do not show clear patterns that can easily be fit to an exponential decay. The 
   correlation length of both sandwiched systems is relatively low because the height of the first
   peak of $g(z)$ is so high. The peak height indicates the degree of local ordering and influences
-  the intensity of R-$pi$. If vertically adjacent sandwiched head groups were less ordered, which
+  the intensity of R-$\pi$. If vertically adjacent sandwiched head groups were less ordered, which
   might be achieved with much longer simulations, then the leading peak intensity should decrease and
   the correlation length would increase. We expect that the leading peak would only get more intense 
-  if monomers stacked 3.7 \AA apart. Conversely, parallel displaced head groups are not as confined
+  if monomers stacked 3.7 \AA~apart. Conversely, parallel displaced head groups are not as confined
   by their vertically adjacent neighbors. This z-direction translational freedom may still be 
-  feasible if monomers stack 3.7 \AA apart in a parallel displaced configuration.
+  feasible if monomers stack 3.7 \AA~apart in a parallel displaced configuration meaning the system
+  would maintain a correlation length and R-$\pi$ intensity in relative agreement with experiment.
 
@@
   the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
-  The monomer head groups in our simulations do not move enough to create the noise which would 
-  cause such behavior. See Section S\ref{S-section:rpi_ft} of the supporting information for
-  illustrative examples.
+  The monomer head groups in our simulations do not move enough on the timescales simulated to 
+  create the noise which would cause such behavior. See Section S\ref{S-section:rpi_ft} of the
+  supporting information for illustrative examples.
 
@@
   and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the correlation functions
-  are nearly identical (See Figure~\ref{S-fig:z_correlation_overlay}).
+  are nearly identical (See Figure~S\ref{S-fig:z_correlation_overlay}).
 
@@
   we know that such a helical configuration will not produce R-double, but only off-axis 
-  reflections at the same $q_z$ value ~\cite{harburn_atlas_1975}. There is not a unique solution
+  reflections at the same $q_z$ value~\cite{harburn_atlas_1975}. There is not a unique solution
   that describes the origin of R-double. Extracting the exact relationship between a diffraction
@@
   We have proposed configurations that result in the appearance of R-double below, and we can 
-  speculate which is makes the most physical sense. We explore both dry and wet configurations.
+  speculate which makes the most physical sense. We explore both dry and wet configurations.
 
@@
   disappears again. Simulated XRD patterns of all other solvated systems tested are shown 
-  in Figure S~\ref{S-fig:solvation}.
+  in Figure S~\ref{S-fig:solvation}, however R-double is not present.
 
@@
   possible that a more realistic forcefield would make the effect stronger or weaker. If 
-  this is truly the mechanism, it implies that the systems studied by Feng et 
-  al.\cite{feng_scalable_2014,feng_thin_2016} were not truly thermotropic Col\textsubscript{h}
-  phases. Rather, they were very low water content H\textsubscript{II} phases unintentionally
+  this is truly the mechanism, it implies that the system studied by Feng et 
+  al.\cite{feng_scalable_2014,feng_thin_2016} was not truly a thermotropic Col\textsubscript{h}
+  phase. Rather, they were very low water content H\textsubscript{II} phases unintentionally
   created due to the neat monomers' hydroscopicity. This detail may be important for reproducing
@@
 
-  The calculate value of ionic conductivity is 5x higher than experiment because 
+  The calculated value of ionic conductivity is 5x higher than experiment because 
   we simulated infinitely long, aligned pores. The ionic conductivity measurement 
@@
   There are minor changes to the physical characteristics of these systems when 
-  they are cross-linked (See Figure ~\ref{fig:xlink}). The ionic conductivity of 
+  they are cross-linked (See Figure~\ref{fig:xlink}). The ionic conductivity of 
   the sandwiched configuration decreases while that of the parallel displaced 
@@
   to a single equilibrium structure. We conducted extensive analysis in order to 
-  isolate structures which most closely resembles the true equilibrium structure.
+  isolate structures which most closely resemble the true equilibrium structure.
 
   We achieve maximum structural consistency with experiment, as determined by simulated
-  2D structure factors, when we build our model in the ordered basin parallel displaced
+  2D XRD patterns, when we build our model in the ordered basin parallel displaced
   configuration with 5 monomer columns per pore and 1 wt\% water. R-alkanes and R-pores

### 2018-06-16 Ben_Manuscripts/structure_paper/Draft.tex
updated draft.

@@
   self-assembled lyotropic liquid crystals (LLCs) are a promising material for
-  selective separations. In this work, we develop an atomistic molecular model
-  of an experimentally characterized LLC membrane. While it is relatively 
-  straightforward to create a stable hexagonal phase model, we demonstrate that 
-  closely reproducing the experimental pore structure requires a carefully 
-  constructed initial configuration in order to avoid falling into metastable
-  basins. We use simulated X-ray Diffraction (XRD) patterns in order to ensure 
+  selective separations. In this work, we investigate an experimentally characterized 
+  LLC membrane using an atomistic molecular model. 
+  %MRS8: I think this is a little too subtle a point to be making for the abstract. 
+  %I added a bit different spin on this at the end of the abstract to gesture towards the idea. Thoughts?
+  %While it is relatively 
+  %straightforward to create a stable hexagonal phase using atomistic modeling, we demonstrate that 
+  %closely reproducing the experimental pore structure requires a carefully 
+  %constructed initial configuration in order to avoid falling into metastable
+  %basins. 
+  We use simulated X-ray diffraction (XRD) patterns in order to ensure 
   maximum consistency between our structures and experiment. We show that pores 
@@
   nanopores and reveal that there exists a composition gradient rather than a 
-  hard partition between the hydrophilic and hydrophobic regions. The clearer 
-  picture of the nanoscopic structure of these membranes provided in
+  abrupt partition between the hydrophilic and hydrophobic regions. A caveat is 
+  that the time scales of the dynamics are extremely long for this system, 
+  requiring starting from a range of alternative initial configurations and 
+  careful examination of the metastable states observed.
+  The clearer picture of the nanoscopic structure of these membranes provided in
   this study will enable a better understanding of the mechanisms of small 
   molecule transport within these nanopores.
-
   \end{abstract}
@@
   % BJC5: Note to self -- how to use latex xr : Figure S~\ref{S-fig:monomer_color_coded}
+
+  % MRS8: intro still seems a bit limited, describe more generally
+  % (and briefly!) other things selective membranes are good for. The
+  % paper is primarily about selective membranes, not fracking
+  % water. See elimalech paper for reviews, and add a number of more
+  % citations.
 
@@
 
-  % MRS: abstract seems a bit limited, describe more generally (and
-  % briefly!) other things selective membranes are good for. The paper is primarily about selective membranes, not fracking water.  
-  % It seems out of       balance to be talking about only one application.
-
 %  The permeability-selectivity tradeoff is a well-known problem in the membrane
@@
 % MRS7: Do a pass for clarity at the sentence level.  For example ``degree of stochasticity'' is vague.
+% MRS8: ``because they are unstructured'' lacks detail.  NF has some structure, since there are irregular pores. Check some other reviews and see the points they cover?
   Current commercial RO and NF membranes suffer limitations to their selectivity
@@
 
+%MRS8: preliminary evidence has shown they may be?  It's more than a guess.
   Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
@@
   cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
-  described in this paper are salts, and therefore lead to Donnan exclusion of ions
+  examined in this paper are salts, and therefore lead to Donnan exclusion of ions
   in solution. The membrane gains a net surface charge when counterions from the head
@@
   %thereby permitting the design of solute-specific separation membranes
-  %\cite{humplik_nanostructured_2011}. One can acheive most membrane-based aqueous separations of
+  %\cite{humplik_nanostructured_2011}. One can achieve most membrane-based aqueous separations of
   %small molecules using reverse osmosis (RO) or nanofiltration
@@
   the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
+  %MRS8: maybe say what it is, not just what it's named? 
   Current experimental efforts are focused on extending the method to the 
@@
 % the software I used to create it
+%MRS8: sound good.
   \begin{figure}
@@
   chemical space available to design monomers for creation of separation-specific
-  membranes. A good molecular model should incorporate a detailed picture of the
+  membranes. Useful molecular-level modeling should incorporate a detailed picture of the
   nanoscopic pore structure which is crucial to understanding the role of
-  monomer structure in solute transport and membrane design. Models resulting
-  from molecular dynamics simulations can provide the required level of detail
+  monomer structure in solute transport and membrane design. 
+Atomistic molecular dynamics simulations can provide the required level of detail
   (Figure \ref{fig:detail}), assuming the force fields are sufficiently accurate.
@@
   %BJC6: is this too bold considering the work done at University of Wisconsin?
-  In this study, we build a significantly more realistic atomistic model of LLC
+  %MRS8: Maybe take out significantly
+  In this study, we achieve a %significantly 
+  more realistic atomistic description of LLC
   membranes than, to our knowledge, has ever previously been created, and explore
   what new structural information can be gained and what structure hypotheses are
-  supported by this model. We validate the model using as much experimental
+  supported by this model. We validate the results using as much experimental
   information as possible. We are most interested in reproducing the conclusions
@@
     \caption{(a) Previous understanding of the pores are essentially speculations 
-    based on limited chemical and experimental data. (b) We use a detailed molecular 
-    model in this paper in order to appropriately model the pore's complex architecture
+    based on limited chemical and experimental data. (b) We use detailed molecular 
+    modeling in this paper in order to appropriately model the pore's complex architecture
     which is crucial to understanding the mechanism of solute transport. In both 
@@
 
-  In this paper, we develop a molecular model of the Col\textsubscript{h} assembly 
+  In this paper, we perform molecular modeling of the Col\textsubscript{h} assembly 
   formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-  phase is a simpler starting point. The system has no water which allowed us
-  to simulate longer timescales, and there exists detailed experimental
+  phase is a simpler starting point. The system 
+  %MRS8: check rephrasing on this, since we do say later it does have some water
+  %has no water 
+  is not assembled in aqueous phase
+  which allowed us to simulate longer timescales, and there exists detailed experimental
   characterization of the fully aligned state, including 2D wide-angle X-ray
   scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
-  structural data. We will use this Col\textsubscript{h} model in order to build an 
-  H\textsubscript{II} model in the future.
+  structural data. 
+  %MRS8: I started tweaking the below, but it might be better just to eliminate.
+  % Modeling of Col\textsubscript{h} will help in modeling 
+  %H\textsubscript{II} in the future.
   %The two phases appear to share similar structural characteristics since the
@@
 	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
-	rings along the z axis\cite{feng_scalable_2014}, meaning that if one traces the 
+	rings along the $z$ axis\cite{feng_scalable_2014}, meaning that if one traces the 
 	positions of the aromatic rings with a helical curve, then for each full turn 
@@
   Despite having structural data, there is still information which experiment cannot
-  definitively answer. There are a number of structural questions we wish to answer in this 
-  article. We want to know:
+  definitively answer. 
+  %MRS8: grammatically a bit redundant.
+  %There are a number of structural questions we wish to answer in this article. 
+  Specifically, we want to know:
   \begin{enumerate}
@@
  	hexagonal array of pores (xy plane) and short range z-direction correlations between 
-        stacked columns of monomers. In this study, we use our atomistic molecular model
+        stacked columns of monomers. In this study, we use atomistic molecular modeling
         to study how the system's structure is affected by the density of these monomer columns
@@
 	On the short timescales accessible to MD (even the 100's of nanoseconds of simulation 
-	peformed here are short compared to experimental timescales), we observe distinct metastable
+	performed here are short compared to experimental timescales), we observe distinct metastable
 	configurations which depend on starting configuration. We simulated XRD patterns of our system and 
@@
 
-	%BJC5: I could add brief references to other LLC studies which look at hexagnoal phase, but
+	%BJC5: I could add brief references to other LLC studies which look at hexagonal phase, but
 	% without scrutinizing the structural details. In other words, other authors have gotten 
@@
 	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
-	ambient water are leached into the system. The hydrogen bonding network formed by the 
+	ambient water are 
+        %leached 
+        absorbed
+        into the system. The hydrogen bonding network formed by the 
 	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
@@
 
-	\item What is the chemical composition of the pores?\label{point:composition}
+	\item What is the 
+          %MR8: chemical composition is a bit ambiguous; implies mole fractions, which isn't what we mean
+          %chemical composition 
+          detailed atomistic structure of the pores?\label{point:composition}
 
@@
   configuration from the trajectory which we used for full system
-  construction (Figure~\ref{fig:python}a). See section S\ref{S-section:parameterization} 
-  for further detail.
+  construction (Figure~\ref{fig:python}a). See section S-\ref{S-section:parameterization} 
+  for further detail of the parameterization process.
 
@@
   \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system (See section S\ref{S-section:self_assembly}). 
+  indicators of progress towards an ordered system (see section S-\ref{S-section:self_assembly}). 
   To bypass the slow self-assembly process, we use Python scripts to assemble monomers
@@
   and to obtain sufficient resolution when simulating XRD patterns (see further discussion
-  in section S\ref{S-section:monomers_per_column}).
+  in section S-\ref{S-section:monomers_per_column}).
 
@@
   which require careful consideration while placing monomers. The equilibrium
-  configuration is sensitive to some while insensitive to others. The starting
+  configuration is sensitive to some while insensitive to others. We find the starting
   pore radius, defined as the distance of a chosen head group carbon from the
-  pore's central axis, does not influence the equilibrium structure if one choses
+  pore's central axis, does not influence the equilibrium structure if one chooses
   a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
@@
   of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
-  Supporting information, section S\ref{S-section:initial_config_dependence}. The 
+  Supporting information, section S-\ref{S-section:initial_config_dependence}. The 
   distance between vertically stacked monomers, the xy position of monomers with respect 
@@
   \AA. However this spacing yields non-physical behavior which is detailed in the 
-  Supporting Information, section S\ref{S-section:initial_dbwl}.
+  Supporting Information, section S-\ref{S-section:initial_dbwl}.
 
@@
   of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See Figure 
-  S~\ref{S-fig:stacking} for a detailed illustration of the initial configurations in each mode.
+  S-\ref{S-fig:stacking} for a detailed illustration of the initial configurations in each mode.
 
@@
   followed by NPT equilibration simulations run for at least 400 ns using the 
-  Parrinello-Rahman barostat. More precise details are available in 
-  section S~\ref{S-section:equilibration}.
+  Parrinello-Rahman barostat. 
+  %More precise details are 
+  More equilibration details are 
+  available in 
+  section S-\ref{S-section:equilibration}.
 
@@
   % differentiate between ordered/disordered basins?
+  %MRS8: I think this is fine, since it's a relatively standard measure. 
 % \subsubsection{\textit{The nematic order parameter}}\label{method:nematic_order}
@@
   average distance between stacked monomers, and an amplitude that decays exponentially
-  (See Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
+  (see Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
   length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
@@
   %BJC5: in case there is an criticism of this method
-  %The simplest way to do so, would be to fourier transform
-  %$g(z)$ and extract the highest amplitude frequency of the resulting fourier series. 
-  %However, the size of our system limits the width of the bins in fourier space. The bins
+  %The simplest way to do so, would be to Fourier transform
+  %$g(z)$ and extract the highest amplitude frequency of the resulting Fourier series. 
+  %However, the size of our system limits the width of the bins in Fourier space. The bins
   %are too large to extract a precise value of $\mathit{d}_equil$. Instead, 
@@
   atoms in each group from the pore centers, then normalized by the volume of the
-  annulus defined by the bin edges and the z box vector (See Figure~S\ref{S-fig:rdf_diagram}).
+  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}).
 
@@
 
+  %MRS8: we should ask Matt see if we can give the github repository
+  %for the XRD determination in the paper for reproducibility. I will do that. 
   We generated simulated XRD patterns based on atomic coordinates in order to make
-  a direct experimental comparison. We modelled all atomic coordinates as Gaussian
+  a direct experimental comparison. We modeled all atomic coordinates as Gaussian
   spheres of electron density corresponding to each atom's electronic radius. A 
@@
   alkane-alkane density, averaged over all angles, is the feature most likely to be
-  replicated between experiment and simulation. Other features are dependent on 
+  replicated between experiment and simulation, as atomistic alkane parameters are 
+  relatively well studied. Other features are dependent on 
   system ordering which is likely to have some dependence on initial configuration. 
@@
   measured ion concentration with respect to the volume of the entire unit cell. 
+  More details are provided in the Supporting Information, Section~S-\ref{section:ionic_conductivity}.
 
@@
   We based our cross-linking algorithm on the known reaction mechanism 
-  (Figure S\ref{S-fig:xlink_mech}). The reaction takes place at the terminal vinyl groups
+  (Figure S-\ref{S-fig:xlink_mech}). The reaction takes place at the terminal vinyl groups
   on each alkane tail. The procedure is carried out iteratively. Each iteration, the
@@
   the measured equilibrated pore-to-pore distances. To discern the composition of
-  the monomer layers, addressing question \ref{point:monomernum}, we ran
+  the monomer layers, addressing question \ref{point:monomernum} above, we ran
   simulations of systems created with 4--8 columns per pore. We built systems in both
@@
   spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional 
-  systems with monomers initially spaced 5 \AA~apart vertically (See section~\ref{S-section:initial_pore_spacing}
-  of the supporting info for more details on sensitivity to initial layer spacing). 
+  systems with monomers initially spaced 5 \AA~apart vertically (see section~\ref{S-section:initial_pore_spacing}
+  of the Supporting Information for more details on sensitivity to initial layer spacing). 
   We considered the pore-to-pore spacing to be equilibrated as defined in section~\ref{method:equil_time}.
@@
   nanosecond simulated here. For simplicity, we group the systems studied here into the ordered
-  and disordered basins. Any system where $\mathit{d}=3.7$ \AA~will be included in the
-  ordered basin and any system where $\mathit{d}=5.0$ \AA~will be included in the disordered basin.
+  and disordered basins. What we find is that any system where $\mathit{d}=3.7$ \AA~can generally 
+  be characterized as being in an
+  more ordered basin, and any system where $\mathit{d}=5.0$ \AA~can be characterized as a more the disordered basin.
   Generally, when monomers are started further apart, they stay further apart than systems where
@@
   extra space between stacked monomers, monomer head groups have more rotational freedom. We
-  quantified the ordering of the head groups using the nematic order parameter (See section S~\ref{method:nematic_order}). 
+  quantified the ordering of the head groups using the nematic order parameter (see section S~\ref{method:nematic_order} for details of calculation). 
+  %MRS8: the reference above isn't appearing. I'm not sure why after quick check.
   Disordered basin systems have a lower nematic order parameter (meaning they are more disordered) 
@@
   6 columns per pore, have an equilibrated pore spacing ca. 0.50 nm higher than experiment.
-  Monomers in disordered basin systems built with 6 columns-per-pore agree with experiment 
+  Monomers in disordered basin systems built with 6 columns-per-pore agree with experimental pore-to-pore distances 
   within error, but stack too far apart. Those in the disordered sandwiched and disordered
-  parallel displaced configurations stack $\approx$ 4.87 and 4.94 \AA~apart respectively, 
+  parallel displaced configurations stack $\sim$4.87 and 4.94 \AA~apart respectively, 
   which is ca. 1.2~\AA further apart than suggested by experiment. 5 column-per-pore systems
@@
 % Our methodology for calculating equilibrium stacking distance is fully explained in section~\ref{section:rpi}.
-
+% MRS8: sounds good.  
 %  Relative to ordered basin 
@@
   their respective metastable basins. By sampling more uncorrelated equilibrium configurations,
-  we can suppress some of the noise (See section S\ref{S-section:xrd_noise}).
+  we can suppress some of the noise (See section S-\ref{S-section:xrd_noise}).
 
@@
 	interest are presented in Table~\ref{table:relative_inensities_300K}. In both XRD patterns generated
-	from parallel displaced patterns, there is a faint line across $q_z \approx 0.7~$\AA$^{-1}$, half
+	from parallel displaced patterns, there is a faint line across $q_z \sim 0.7~$\AA$^{-1}$, half
 	the simulated value of R-$\pi$. Although it does not cross through $q_r = 0$~\AA$^{-1}$, it is at 
@@
   defects and domain misalignment which decreases the overall intensity.
-  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
+  % MRS4: comments from Matt suggest that domain misalignment shouldn't alone be responsible for 
   % the difference in intensity ratio. Some of the experiments should help explain it better. 	
@@
   $q_r = 0~\AA^{-1}$ so it does not necessarily appear for the same reason as R-double. 
-  This type of pattern is characteristic of a helix ~\cite{watson_structure_1953}. The 
+  This type of pattern is characteristic of a helix~\cite{watson_structure_1953}, as the 
   head groups in the parallel displaced configuration are arranged in a helix.
@@
   agrees with experiment. There is no R-double intensity to be measured. Figures
-  are provided in section S\ref{S-section:xrd_intensities} to make these measurements clear.
+  are provided in section S-\ref{S-section:xrd_intensities} to make these measurements clear.
 
@@
 %  than in the experimental pattern. The simplest reason is that R-$\pi$ and
-%  R-alkanes add together to boost the overall signal at interesecting values of
+%  R-alkanes add together to boost the overall signal at intersecting values of
 %  $\mathbf{q}$. In addition, we observe a much higher maximum intensity within
@@
 Not clear how the angle averaging obscured this before?
-%  %BJC2 From plots of raw structure factor, it doesn't seem like a normalization issue. It was probably obscured in the orginal angle averaging because it 
+%  %BJC2 From plots of raw structure factor, it doesn't seem like a normalization issue. It was probably obscured in the original angle averaging because it 
 %  % was averaged with neighboring bins
@@
   explain R-spots. 
-
-  To understand the true origin of R-spots, we determined which atoms gave rise to the 
-  feature. Since R-spots is present as higher intensity spots within R-alkanes, it is
+  %MRS8: did you do a few different things here as sensitivity analysis to show that the finding was robust?  If so, putting some of that in would be useful.
+
+  To understand the %true 
+  more likely origin of R-spots, we determined which atoms gave rise to the 
+  feature. 
+  %MRS8: next two sentences repetitive; could you revise? 
+  Since R-spots is present as higher intensity spots within R-alkanes, it is
   likely that the spots arise as a consequence of the tails. By removing all non-tail atoms
@@
 %  		may not correctly model the behavior of the tails at 300 K (citation?).
-%                % look for papers on protien folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
+%                % look for papers on protein folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
 %  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
@@
   \end{subfigure}
+  %MRS8: nicely organized figure! I think in (c), you do want the red/green dots showing hexagonal symmetry to be bigger; 
+  %when the figure is reduced they are hard to see.
   \caption{(a) R-spots increases in intensity when the temperature of the system is 
@@
 
-  There is not a single reason for the high intensity of R-$\pi$ in our simulations.
+  There is not a single reason we can clearly identify for the high intensity of R-$\pi$ in our simulations.
   We used one-dimensional pair distribution functions of the centers of masses of monomer
   phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
-  columns and the degree to which they are correlated. These metrics helped us disect the 
+  columns and the degree to which they are correlated. These metrics helped us dissect the 
   various contributions to R-$\pi$. Figure~\ref{fig:correlation} shows $g(z)$ for all 
@@
   disordered basin in the sandwiched and parallel displaced configurations respectively. 
-  The distance between stacked monomers is greater than experiment by 0.5 - 0.9 \AA~across all 
+  The distance between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all 
   cases. This behavior is not surprising since GAFF models atoms as point charges and does not 
@@
   by their vertically adjacent neighbors. This z-direction translational freedom may still be 
-  feasible if monomers stack 3.7 \AA~apart in a parallel displaced configuration meaning the system
+  feasible if monomers stack 3.7 \AA~apart in a parallel displaced configuration, meaning the system
   would maintain a correlation length and R-$\pi$ intensity in relative agreement with experiment.
@@
   The monomer head groups in our simulations do not move enough on the timescales simulated to 
-  create the noise which would cause such behavior. See Section S\ref{S-section:rpi_ft} of the
+  create the noise which would cause such behavior. See Section S-\ref{S-section:rpi_ft} of the
   supporting information for illustrative examples.
@@
   and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the correlation functions
-  are nearly identical (See Figure~S\ref{S-fig:z_correlation_overlay}).
+  are nearly identical (See Figure~S-\ref{S-fig:z_correlation_overlay}).
 
@@
 %  For reasons we will develop in the next segment of our
-%  discussion, configurations intially built with layers stacked 5.0 \AA~apart 
+%  discussion, configurations initially built with layers stacked 5.0 \AA~apart 
 %  will be grouped into the disordered pore basin, while those built with layers
@@
 %		notably in the region bounded by R-alkanes. The disordered pore
-%		systems started in the parallel displaced configuariton (c) does not show R-spots
+%		systems started in the parallel displaced configuration (c) does not show R-spots
 %		or R-$\pi$ which suggests that head groups are not associating with each other
@@
 %  from experimental evidence. The experimental correlation length (See
-%  Suppporting Information for details its derivation) suggests that layers are
+%  Supporting Information for details its derivation) suggests that layers are
 %  correlated with about 3 neighboring layers which is closer to the values
@@
 %  We can produce R-double if our initial configuration contains alternating parallel and
-%  antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
+%  anti-parallel carboxylate groups relative to the plane of the monomer's phenyl ring.
 %  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). It is difficult to physically
@@
 %  of carboxylate groups attached to phenyl rings since the group extends the system's 
-%  $\pi$ conjugation (citation) (See Figure S\ref{S-fig:carboxylate_dihedral_rb}).
+%  $\pi$ conjugation (citation) (See Figure S-\ref{S-fig:carboxylate_dihedral_rb}).
 %  
@@
   knowledge, there have been no studies that specifically address the possibility of a
-  configuration like this. Our forcefield causes our system to tend towards uniformly spaced
+  configuration like this. 
+  %MRS8: above: be more precise, for example, QM studies or crystallographic investigation of stacked pi-pi system, 
+  % can cite the reference found.
+  Our force field causes our system to tend towards uniformly spaced
   layers.   Simulations of unevenly spaced systems are only stable if position restraints
   are applied to heavy atoms of the phenyl rings.
-
-  Adding water to the system facilitates the appearance of R-double. We added water to the 
+  %MRS8: added below.
+  There is little evidence from QM studies of stacked $\pi-\pi$ systems that this behavior is incorrect.~\ref{???}
+
+  Adding water to the system 
+  %facilitates 
+  appears to facilitate 
+  the appearance of R-double,
+  %MRS8: added above.
+I realize the H-bonding isn't brought up until later paragraphs, but I don't want to leave people in suspense; it serves as essentially a thesis of the next few paragraphs, which do group together.
+  through the creation of hydrogen bonding of water to carboxylate groups of consecutive layers.
+  We added water to the 
   parallel displaced and sandwiched configurations in the ordered basin and equilibrated them
@@
 
-  R-double appears in the solvated system due to the structure of the head groups. To prove this,
+  R-double appears in the solvated system due to the structure of the head groups. To 
+  %prove 
+  demonstrate
+  this,
   we removed the head groups from the trajectory used to produce Figure~\ref{fig:solvated_pore_rzplot_norestraints}
@@
   lead to R-double (much like the configuration in Figure~\ref{fig:staggered_rzplot_norestraints}). There are
-  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
+  a modest number of occurrences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
   Peaks in the distributions represent the scenario where a monomer head group shares a 
   water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
-  we calculated the discrete fourier transform of the distributions which we used as a rough 
+  we calculated the discrete Fourier transform of the distributions which we used as a rough 
   indicator of whether the head group arrangement will lead to R-double. We see the 
@@
 
-  It is likely that R-double originates from water molecules as described above and it is the 
-  only mechanism that occurred without using position restraints. The extent of the hydrogen
+  It is thus most likely that R-double originates from water molecules as described above, as it is the 
+  only mechanism that can be observed without externally restraining positions. The extent of the hydrogen
   bonding network that forms is largely determined by the accuracy of the forcefield. It is 
@@
   phase. Rather, they were very low water content H\textsubscript{II} phases unintentionally
-  created due to the neat monomers' hydroscopicity. This detail may be important for reproducing
+  created due to the neat monomers' hydroscopicity. This detail may therefore be important for reproducing
   the results of Feng et al.
@@
   spaced in the z-direction since they are pulled closer together by hydrogen bonds. 
-  (d) We performed discrete fourier transforms on each distribution in (c). In all cases,
+  (d) We performed discrete Fourier transforms on each distribution in (c). In all cases,
   the strongest peak represents periodicity every layer. In Pore 1, there is also periodicity
@@
 
-  \subsection{Chemical composition of pore columns}
+  \subsection{Atomistic structure of pore columns}
 
@@
   %BJC6: moved this paragraph up to make the section more idea-focused
-  In general, the composition of each region, particulary within our definition of 
-  the pore region, is similar between all systems. We believe we can solvate and study transport
-  in any of the systems presented here and extract similar transport mechanisms. We will 
-  need to verify that this assumption is true.
+  In general, the composition of each region, particularly within our definition of 
+  the pore region, is similar between all systems. 
+  %MRS8: weakened a bit
+  This suggest that the details of transport may be relatively independent of the structural differences between
+  different possible structures studied here.
+  %We believe we can solvate and study transport
+  %in any of the systems presented here and extract similar transport mechanisms. We will 
+  %need to verify that this assumption is true.
 
@@
   region, we used heavy atoms making up the aromatic rings and carboxylate groups. For the tail
-  region we used carbon atoms of the monomer tails (See Figure S\ref{S-fig:monomer_color_coded}
+  region we used carbon atoms of the monomer tails (See Figure S-\ref{S-fig:monomer_color_coded}
   for a diagram). We averaged the histograms over at least 50 ns of equilibrated trajectory.
@@
   to the hydrophobic region, rather than an abrupt division. Based on size-exclusion 
-  experiments, we define the pore radius to be 0.6 nm
+  experiments, we define the pore radius to be 0.6 nm~\cite{zhou_supported_2005}. 
   %BJC5 : Add vertical line to plots for 'pore radius'? Might be too busy.
-  ~\cite{zhou_supported_2005}. The system does not confine
+  %MRS8: I actually think it might add understanding  I would label it as ``experimentally estimated size-exclusion radius''.
+  The system does not confine
   sodium ions and head groups to just within the pore region. For dry systems,
@@
 %  fit through. We leave these investigations for a future study.
-  %MRS7: or could say that the size could be different depending on the the nature of the molecle. Could bring up
+  %MRS7: or could say that the size could be different depending on the the nature of the molecule. Could bring up
   %Sarah's results with different selectivity of molecules about the same size.
@@
   %BJC6: redone with only tops of histograms plotted, and water added
+  %MRS8: this is good at showing most structures are the same.
+It would be nice to also see how different components relate to each other spatially.
+Perhaps you can add a picture (can pick just one, since they are so similar) and plot the different components on one plot to show how the gradients intersect.
   \begin{figure}[!htb]
@@
 	  head groups, even when the system is solvated. This architecture may impede transport in 
-	  the real system. The solvated system has a lower density of head groups near the 
+	  the real system in a chemically-dependent manner. 
+          The solvated system has a lower density of head groups near the 
 	  pore center which is likely due to the swelling that is necessary in order to fit water
@@
 %  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
-%  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
+%  a modest number of occurrences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
 %  Peaks in the distributions represent the scenario where a monomer head group shares a 
 %  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
-%  we calculated the discrete fourier transform of the distributions which we used as a rough 
+%  we calculated the discrete Fourier transform of the distributions which we used as a rough 
 %  indicator of whether the head group arrangement will lead to R-double. We see the 
@@
   head groups and the ether oxygens which attach the tails to the head group 
-  (See Figure S\ref{S-fig:dihedrals}). We exclude the dihedral from the middle tail 
+  (See Figure S-\ref{S-fig:dihedrals}). We exclude the dihedral from the middle tail 
   since it is fundamentally different than the two symmetric outside tails. We 
@@
   is raised. At 300K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
-  not cross the x-axis until $\approx$ 105 ns meaning that tails might only fully rotate
-  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
+  not cross the x-axis until $\sim$105 ns meaning that tails fully rotate on average about 
+  times over the course of the 400 ns that we studied. Additionally, the correlation 
   function plateau's near a value of -0.2 which indicates that the tails are starting in 
   an unfavorable configuration. We implemented distance restraints between the centers of 
-  mass of monomer head groups to preserve the hexagonal phase, then rose the temperature 
+  mass of monomer head groups to preserve the hexagonal phase, then raised the temperature 
   of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
-  decorrelation of the ether dihedrals after $\approx$ 11 ns with a plateau at 0, 
+  decorrelation of the ether dihedrals after $\sim$11 ns with a plateau at 0, 
   (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
@@
 % stuff to SI and summarize briefly. But it I think it makes what we did more abstract.
+%MRS8: I think that you can just give the numbers  in the text, and move the figures to SI? Figures don't add a lot.
 
@@
 
-  \subsection{Model Ionic Conductivity Measurements}
+  \subsection{Ionic Conductivity Measurements}
 
@@
 For diffusion, you can do just one calculation, and put the alternate method in SI (you can mention you did it, i.e.
-we did X, it was noiser, but agreed within data (see SI).
+we did X, it was noisier, but agreed within data (see SI).
 
@@
   one order of magnitude of experiment (Figure~\ref{fig:ionic_conductivity}). We
-  verified the value calculated by the Nernst-Einstein relationship using a 
-  second method called the collective diffusion model\cite{liu_collective_2013} 
+  verified the value calculated by the Nernst-Einstein relationship using 
+  the collective diffusion model\cite{liu_collective_2013} 
   (See section S~\ref{s-fig:conductivity}). The values calculated by the 
+  %MRS8: this section reference not working either.
   collective diffusion model agree with Nernst-Einstein  values within error, 
@@
 
-  We applied our cross-linking algorithm to equilibrated sandwiched and parallel
+  Experimentally, membranes are crosslinked for mechanical stability before use. We applied 
+  our cross-linking algorithm to equilibrated sandwiched and parallel
   displaced configurations in the ordered pore basin. We allowed the cross-linking
   algorithm to propagate until greater than 90\% of vinyl groups were either involved
-  in a cross-linking reaction or were terminated. See section S\ref{S-section:xlink}
-  for further details on the cross-linking algorithm. We allowed the cross-linked
+  in a cross-linking reaction or were terminated (see section S-\ref{S-section:xlink}
+  for further details of the cross-linking algorithm). We allowed the cross-linked
   configurations to simulate for 100 ns further in the NPT ensemble.
@@
   % BJC5: Is it worth including the distance between layers and the correlation length? 
-  There are minor changes to the physical characteristics of these systems when 
+  % MRS8: probably very briefly discuss the changes, to justify the use of the word ``minor''
+  There are only minor changes to the physical characteristics of these systems when 
   they are cross-linked (See Figure~\ref{fig:xlink}). The ionic conductivity of 
@@
 
-  \section{Conclusion}
+  \section{Conclusions}
 
@@
 Or ``observation Y in the simulations supports the conclusion Y''.
-  We have used a detailed molecular model of the Col\textsubscript{h} phase
+  We have used detailed molecular modeling of the Col\textsubscript{h} phase
   formed by Na-GA3C11 in order to study its nanoscopic structure. While there
@@
   We explored two classes of metastable basins which are dependent on the initial
-  vertical stacking distance between monomers : the ordered and disordered pore basins.
+  vertical stacking distance between monomers: the ordered and disordered pore basins.
   We expect that these metastable configurations will eventually rearrange and converge
@@
   configuration with 5 monomer columns per pore and 1 wt\% water. R-alkanes and R-pores
-  appear where expected for the reasons originally predicted. We learned that R-spots
+  appear where expected for the reasons originally predicted. We find that R-spots
   is likely due to ordered alkane chain packing. R-$\pi$ appears at lower q values than
   experiment because monomer stack too far apart. Finally, we observed that our model
-  reproduces R-double only when we add 1 wt\% water to the system. This observation has
-  important implications for the reproducibility of the experimental results from Feng 
+  can only produce
+  %reproduces 
+  R-double when we add 1 wt\% water to the system. This observation has
+  %important 
+  possible
+  implications for the reproducibility of the experimental results from Feng 
   et al since they claim that their membrane is completely dry.
@@
   ions. All dry systems studied showed a similar distribution of sodium, head groups 
-  and tails while the wet system shows evidence of swelling due to the presence of 
-  water molecules. We also observed that there is not a hard partition between hydrophlic
+  and tails while the wet system shows evidence of 
+  %MRS8: modified; water isn't changing things very much.
+  slight
+  swelling, with minor changes in the distributions due to the presence of 
+  water molecules. We also observed that there is not a hard partition between hydrophilic
   and hydrophobic regions, rather there is a gradient. This finding has raised questions
   about the nature of size-exclusion separations in systems without a well-defined pore 
-  size.
+  size, which potentially could give rise to separations that vary with chemical identity as well as size.
 
@@
 
-  We justified that our system can reasonably estimate ionic conductivity.  Our
+  %We justified that 
+  Our system can reasonably estimate ionic conductivity.  Our
   calculations are about 1 order of magnitude higher than experiment, however
@@
   of ca. 1.5, in closer agreement with experiment, the pore spacing decreases and
-  the membrane becomes thicker.
+  the membrane becomes thicker; 
+  %MRS8: added some.
+  however, all changes are relatively minor, preserving most of the features well.
 
 %MRS6'' isn't it 1-3 orders of magnitude lower?
-You cite some slower statistics, and there might be differences between lyotrpic and thermotropic, if the hydrophilic/hydrophobic effect is stronger than the effects in thermotropic fluids.
+You cite some slower statistics, and there might be differences between lyotropic and thermotropic, if the hydrophilic/hydrophobic effect is stronger than the effects in thermotropic fluids.
 %  We acknowledge that our simulated system exhibits glassy dynamics. The
@@
 
-  With the structural understanding gained by these simulations, we will
-  evaluate transport of various solutes within the system. We will apply the
+  %MRS8: better to rephrase what can be done (which is a present thing) instead of what we will do (which is future and undetermined).
+  With the structural understanding gained by these simulations, 
+  %we will
+  it becomes possible
+  evaluate transport of various solutes within the system, and apply the
   knowledge gained from this study in order to suggest improvements to the
@@
 % LocalWords:  gimp disassociate pore's barostat racemic colorbars Nernst LLCs
-% LocalWords:  entropic rzplot transitioning spoel github pymbar Yelk Glaser
+% LocalWords:  entropic rzplot transitioning spoel github pymbar Yelk Glaser xr
+% LocalWords:  flowback FW wastewaters wastestream fracking semipermeable TFC
+% LocalWords:  solute's polymerized wijmans diffusivities amphiphilic MWCO Ia
+% LocalWords:  nanostructures bicontinuous hatakeyama tortuosity Pn hII TLC ing
+% LocalWords:  microstructures multilayer Xunda's refamiliarize nanostructure
+% LocalWords:  nanoscale TEM LC methacrylated Eq scipy equil xz meridional phys
+% LocalWords:  semiisotropic nocbar chem waxs ish fb entropically steric vv rpi
+% LocalWords:  highlimit yz nematically carboxylate norestraints rb Bushey cyan
+% LocalWords:  dihedrals cbar adenine carboxyl sterically QM hydroscopicity LCs
+% LocalWords:  nophenyls nowater hbonds notails decorrelated Decorrelating SI
+% LocalWords:  xlink uncross

### 2018-06-16 Ben_Manuscripts/structure_paper/supporting_information.tex
spellchecking.

@@
 \externaldocument[M-]{draft}
-
+%MRS8: can use document class here - looks weird with title/authors as written.
 \title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
@@
   Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
-  box with a volume of 660 $nm^3$, 25 \% larger than those used to create ordered unit
-  cells we studied. We tested systems with semiisotropic and anisotropic pressure 
+  box with a volume of 660 $nm^3$, 25\% larger than those used to create ordered unit
+  cells we studied. We tested systems with semi-isotropic and anisotropic pressure 
   coupling since the shape of the unit cell will likely need to change in order to 
-  accomodate hexagonally packed pores.
-
-  We use the nematic order paramter as defined in section~\ref{method:nematic_order} to 
+  accommodate hexagonally packed pores.
+
+  We use the nematic order parameter as defined in section~\ref{method:nematic_order} to 
   observe any progress towards system ordering. In both cases, we see that the nematic
@@
 	editconf}. The monomer was centered in the box with edges of the
-	box spaced at least 3 nm from the monomer on all sides. We ran an energy minimzation
+	box spaced at least 3 nm from the monomer on all sides. We ran an energy minimization
 	on the system with the steepest descent algorithm. Next we performed an NVT
@@
   to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
-  patterns. The size of the fourier space bin in each dimension is determined by 
+  patterns. The size of the Fourier space bin in each dimension is determined by 
   $dfrac{2\pi}{L}$ where L is the length of a given box vector. The z-box vector 
@@
 		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
-		have a test system with an intial spacing below the experimental value. As soon
-		as the restraining potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the
+		have a test system with an initial spacing below the experimental value. As soon
+		as the restraining potential switches to 56 kJ mol$^{-1}$ nm$^{-2}$, the
 		columns are able to repel resulting in a large jump in pore spacing
@@
 		changes erratically until it begins to settle when the force constants are
-		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
+		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We recommend
 		avoiding a system such as this where vacuum gaps between pore columns are
@@
 	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
-	  Statistics for the pore radii reported were generated from the timeseries
+	  Statistics for the pore radii reported were generated from the time series
 	  representing the average pore radius at each frame. We detected equilibration
@@
 		slightly larger than the equilibrated pore radius of the system simulated with
-		an intial pore radius of 2.5 \AA. After being run through the full dry
+		an initial pore radius of 2.5 \AA. After being run through the full dry
 		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
@@
 	  equilibration times, and it will almost certainly get trapped in a metastable
-	  configuration that bears no resemblence to the experimental profile.
+	  configuration that bears no resemblance to the experimental profile.
 
@@
 		\caption{When layers are initially stacked 10 \AA~apart and the system
-                is equilibrated using the dry equlibration procedure, large vacuum gaps
+                is equilibrated using the dry equilibration procedure, large vacuum gaps
 		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
@@
   unrestrained structure to equilibrate for 5 ns in the NPT ensemble
-  with pressure controlled by the berendsen barostat. Next, we run long NPT
+  with pressure controlled by the Berendsen barostat. Next, we run long NPT
   equilibration simulations for at least 400 ns using the Parrinello-Rahman
@@
   selected by visual inspection. We report the average intensity within the regions 
-  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernable
+  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernible
   spots, we report the average intensity at the intersection of R-alkanes with
@@
   configurations (N). It is expected that the structure factor should resemble
-  a two-dimsional gaussian. We cannot sample enough independent configurations
+  a two-dimensional Gaussian. We cannot sample enough independent configurations
   of our system to completely eliminate noise.
@@
   intensity far from the pattern (high $q$) uniformly. We used a least squares
-  algorithm to fit a lorentzian curve to the data. Only values recorded above
+  algorithm to fit a Lorentzian curve to the data. Only values recorded above
   $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
@@
   L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
-  of the diagonal entry of the covariance matrix of optimized fit paramaters.
+  of the diagonal entry of the covariance matrix of optimized fit parameters.
   We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
@@
   calculated here is really only an upper bound on the correlation length. 
-  % need citations and more on lorentzian parameters
+  % need citations and more on Lorentzian parameters
   \begin{figure}[!htb]
@@
   \caption{(a) We estimated the system's experimental correlation length using a 
-  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a lorentzian curve 
+  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a Lorentzian curve 
   to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
@@
         \includegraphics[width=1\linewidth]{disordered_offset_density.png}
-        \caption{Parallel Displaced, Disorderd Pore Basin}
+        \caption{Parallel Displaced, Disordered Pore Basin}
         \label{fig:disordered_offset_density}
@@
 %        distribution created by measuring the angle between each centroid (e.g. red
-%        in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
+%        in (c)) and its nearest neighbors (e.g. green in (c)) with respect to the xy
 %        plane has distinct spikes near 30\degree, which is consistent with the location
@@
 	  visualized with water molecules and sodium ions removed. Head groups vacate the
-	  pore region leaving an aqeuous solution of water and sodium ions.}\label{fig:water_pores}
-  \end{figure}
-
-  \section{Demonstrative fourier transforms}\label{section:fourier}
+	  pore region leaving an aqueous solution of water and sodium ions.}\label{fig:water_pores}
+  \end{figure}
+
+  \section{Demonstrative Fourier transforms}\label{section:fourier}
 
@@
         \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
-        \caption{The Collective Diffusion model and the nernst-einstein relation yield
+        \caption{The Collective Diffusion model and the Nernst-Einstein relation yield
         agreeing values of ionic conductivity for both types of ordered basin systems 
@@
 \end{document}
+
+% LocalWords:  Na GA Packmol pdb filetype MarvinSketch noauthor nodate GROMACS
+% LocalWords:  atomtypes antechamber inpcrd prmtop acpype py silva gro gmx NVT
+% LocalWords:  editconf molcharge bccsym cyan png dihedrals pore's ca pt xy kJ
+% LocalWords:  kinetically metastable outlier BJC Berendsen barostat Parrinello
+% LocalWords:  Rahman solvated solvate Eq XRD alkanes WAXS exp FWHM mon alkane
+% LocalWords:  transitioning topview rzplot traj binned wt LLC Subharmonics UV
+% LocalWords:  realspace Crosslinking polymerization FRP crosslinking FRPs rb
+% LocalWords:  racemic Nernst carboxylate antiparallel llc

### 2018-06-16 Ben_Manuscripts/structure_paper/supporting_information.tex
Some more changes.

@@
   finite size effects. Even in our 20 monomer-per-column system, axial correlations
-  between stacked monomers persist throughout the entire correlation function (See
+  between stacked monomers persist throughout the entire correlation function (see
   Figure ~\ref{M-fig:correlation}). The correlation function of the system which we
@@
   groups are oriented in the parallel displaced and sandwiched configurations
-  (See Figure~\ref{fig:stacking}). Our model is most consistent with experiment
+  (see Figure~\ref{fig:stacking}). Our model is most consistent with experiment
   when built with 5 monomers per layer, with layers stacked 3.7 \AA~apart in 
@@
 		it closely matches the experimental pore spacing. Again, we observe abrupt
-		repulsion of columns once the restraining potential is switched to 56 KJ
+		repulsion of columns once the restraining potential is switched to 56 kJ
 		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
@@
 		larger than the experimental value. Once the restraining potential reaches 56
-		KJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
+		kJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
 		a linear trend (Figure~\ref{fig:p2p_50}).
@@
 		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
-		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
+		the restraining potential reaches 56 kJ mol$^{-1}$ nm$^{-2}$, the pore spacing
 		changes erratically until it begins to settle when the force constants are
-		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We recommend
+		below 3 kJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We recommend
 		avoiding a system such as this where vacuum gaps between pore columns are
@@
 			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
-			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 KJ
+			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 kJ
 			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
 			experimental value (a) or at the experimental value (b), there is an abrupt
-			change in pore spacing when the position restraints are reduced to 56 KJ
+			change in pore spacing when the position restraints are reduced to 56 kJ
 			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA~apart (c) the pore spacing
 			remains relatively stable. When pores are spaced 50 \AA~apart (d), the pore
-			spacing decreases nearly linearly once the restraints are reduced to 56 KJ
+			spacing decreases nearly linearly once the restraints are reduced to 56 kJ
 			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA~apart (e), so that monomers
 			do not intersect with adjacent pores, and position restraints are reduced to 56
-			KJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
-			when force constants are reduced below 3 KJ mol$^{-1}$ nm$^{-2}$.} 
+			kJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
+			when force constants are reduced below 3 kJ mol$^{-1}$ nm$^{-2}$.} 
 		\label{fig:p2p}
@@
 	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
-	  as the average distance of all carbonyl carbons (See
+	  as the average distance of all carbonyl carbons (see
 	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
@@
 	  \toprule
+          %MRS8: nm to aa conversion error?
 	  Initial Pore Radius & Equilibrated Pore Radius \\
@@
   initial monomer configuration. Every 50 ps, we reduce the force constants by
-  the square root of its previous value. Once the force constant is below 10 KJ
+  the square root of its previous value. Once the force constant is below 10 kJ
   mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
-  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
+  8, 3, 2, 1, and 0 kJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
   unrestrained structure to equilibrate for 5 ns in the NPT ensemble
@@
   \end{subfigure}
-  \caption{The distribution of angles between nematic director vector (See
+  \caption{The distribution of angles between nematic director vector (see
 	  Figure~\ref{fig:director}) and the z-axis averaged over the equilibrated portion
@@
   \vspace{1em}
-  Experimentalists did not measure the correlation length, so we estimated it
-  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
+  Previous experimental studies of these systems did not calculate the correlation length, so we estimated it
+  from the raw 2D WAXS data. We took a slice of the 2D WAXS data along the dashed line in
   Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
@@
   \end{subfigure}
+  %MRS8: at least one of these would be good to put in the main paper.
   \caption{In all cases, the component radial distribution functions exhibit a
@@
   \midrule
-  Sandwiched, Ordered & $1.4\mathrm{e}{-14}$ \\
-  Parallel Displaced, Ordered & $2.0\mathrm{e}{-14}$ \\
-  Sandwiched, Disordered & $2.0\mathrm{e}{-14}$ \\
-  Parallel Displaced, Disordered & $3.5\mathrm{e}{-14}$ \\
+  Sandwiched, Ordered & $1.4 \times 10^{-14}$ \\
+  Parallel Displaced, Ordered & $2.0 \times 10^{-14}$ \\
+  Sandwiched, Disordered & $2.0 \times 10^{-14}$ \\
+  Parallel Displaced, Disordered & $3.5 \times 10^{-14}$ \\
   \bottomrule
@@
   generated from the discrete Fourier transform of the plots in Figure~\ref{fig:theoretical_correlation_functions}. 
-  The maximum intensity of the power spectrum increases by nearly 60 \% when the correlation 
+  The maximum intensity of the power spectrum increases by nearly 60\% when the correlation 
   function does not decay to one. This explains, in part, the large simulated value of the
@@
   fit to $g(z)$ with a similar function that continues to oscillate with the same amplitude
-  as its third peak. (c) The power spectrum of each plot in (b) exhibits a 60 \% increase in
+  as its third peak. (c) The power spectrum of each plot in (b) exhibits a 60\% increase in
   intensity of the peaks when the function does not decay to 1.}\label{fig:rpi_ft}
@@
   \end{subfigure}
-	\caption{Adding 1 wt \% water to the ordered basin dry systems causes an increase in the intensity
+	\caption{Adding 1 wt\% water to the ordered basin dry systems causes an increase in the intensity
 	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
@@
 
-  In the main text, we calculated ionic conductivity using the Nernst Einstein 
+  In the main text, we calculated ionic conductivity using the Nernst-Einstein 
   relationship. We also measured ionic conductivity using a second method, 
@@
         the collective diffusion model because there is inherently less data that 
-        can be used for its calculation. For that reason, we use only the Nernst 
-        Einstein relationship in the main text.}
+        can be used for its calculation. For that reason, we use only the Nernst-Einstein relationship in the main text.}
         \label{fig:conductivity}

### 2018-06-17 Ben_Manuscripts/structure_paper/Draft.tex
Incorporated comments

@@
   self-assembled lyotropic liquid crystals (LLCs) are a promising material for
-  selective separations. In this work, we investigate an experimentally characterized 
-  LLC membrane using an atomistic molecular model. 
-  %MRS8: I think this is a little too subtle a point to be making for the abstract. 
-  %I added a bit different spin on this at the end of the abstract to gesture towards the idea. Thoughts?
-  %While it is relatively 
-  %straightforward to create a stable hexagonal phase using atomistic modeling, we demonstrate that 
-  %closely reproducing the experimental pore structure requires a carefully 
-  %constructed initial configuration in order to avoid falling into metastable
-  %basins. 
-  We use simulated X-ray diffraction (XRD) patterns in order to ensure 
-  maximum consistency between our structures and experiment. We show that pores 
-  are likely composed of 5 columns of stacked LLC monomers which surround each
+  selective separations. In this work, we investigate an experimentally
+  characterized LLC membrane using an atomistic molecular model. We use
+  simulated X-ray diffraction (XRD) patterns in order to ensure maximum
+  consistency between our structures and experiment. We show that pores are
+  likely composed of 5 columns of stacked LLC monomers which surround each
   hydrophilic core. Although this system has been reported as dry, we show that
@@
   requiring starting from a range of alternative initial configurations and
-  careful examination of the metastable states observed.
-  The clearer picture of the nanoscopic structure of these membranes provided in
-  this study will enable a better understanding of the mechanisms of small 
-  molecule transport within these nanopores.
+  careful examination of the metastable states observed. The clearer picture of
+  the nanoscopic structure of these membranes provided in this study will enable
+  a better understanding of the mechanisms of small molecule transport within
+  these nanopores.
   \end{abstract}
@@
   More highly selective membranes would be extremely useful for the recovery of
-  dissolved species in complex aqueous and organic solutions. For example, selective
-  membranes can further progress forward osmosis processes by reducing the cost of 
-  separating potable water from draw solutions~\cite{mccutcheon_novel_2005}. Additionally, 
-  flowback water (FW) produced during hydraulic fracturing is a complex wastewater full
-  of potentially valuable dissolved organic compounds such as acetate 
-  that can be recovered using highly selective membranes \cite{dischinger_application_2017}.
-  Finally, a significant amount of nitrogen and phosphorus from fertilizer is found in 
-  wastewater. Selective membranes offer a route towards low energy nutrient recovery 
-  from these wastewaters which can help sustain fertilizer production and subsequently
-  food production into the future \cite{xie_membrane-based_2016}.
+  dissolved species in complex aqueous and organic solutions. For example,
+  selective membranes can further progress forward osmosis processes by reducing
+  the cost of separating potable water from draw
+  solutions~\cite{mccutcheon_novel_2005}. Additionally, flowback water (FW)
+  produced during hydraulic fracturing is a complex wastewater full of
+  potentially valuable dissolved organic compounds such as acetate that can be
+  recovered using highly selective membranes \cite{dischinger_application_2017}.
+  Finally, a significant amount of nitrogen and phosphorus from fertilizer is
+  found in wastewater. Selective membranes offer a route towards low energy
+  nutrient recovery from these wastewaters which can help sustain fertilizer
+  production and subsequently food production into the future
+  \cite{xie_membrane-based_2016}.
   % as we near peak production of minable phosphorus rock .
@@
 % BJC5: added back below paragraph.  
-% MRS7: Do a pass for clarity at the sentence level.  For example ``degree of stochasticity'' is vague.
 % MRS8: ``because they are unstructured'' lacks detail.  NF has some structure, since there are irregular pores. Check some other reviews and see the points they cover?
@@
 %MRS8: preliminary evidence has shown they may be?  It's more than a guess.
-  Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
-  performing highly selective separations. LLCs are amphiphilic molecules that
-  have the ability to self-assemble into porous nanostructures
-  \cite{smith_ordered_1997} and can be crosslinked to create mechanically
-  strong membrane films with pores on the order of 1 nm in diameter
-  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane pores
-  are uniform in size because they are self-assembled. 
-  Since LLC membranes lack a pore size distribution, they
-  inherently exhibit high selectivity due to their strict molecular weight
-  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
-  examined in this paper are salts, and therefore lead to Donnan exclusion of ions
-  in solution. The membrane gains a net surface charge when counterions from the head
-  groups that line the pore walls escape into the feed solution in an effort to balance 
-  the gradients of concentration and electric potential \cite{donnan_theory_1995}.
+  Preliminary evidence has shown that crosslinked lyotropic liquid crystal
+  (LLC) membranes may be capable of performing highly selective separations. LLCs
+  are amphiphilic molecules that have the ability to self-assemble into porous
+  nanostructures \cite{smith_ordered_1997} and can be crosslinked to create
+  mechanically strong membrane films with pores on the order of 1 nm in diameter
+  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane
+  pores are uniform in size because they are self-assembled.  Since LLC membranes
+  lack a pore size distribution, they inherently exhibit high selectivity due to
+  their strict molecular weight cut-off (MWCO)~\cite{zhou_supported_2005}.
+  Additionally, the LLC monomers examined in this paper are salts, and therefore
+  lead to Donnan exclusion of ions in solution. The membrane gains a net surface
+  charge when counterions from the head groups that line the pore walls escape
+  into the feed solution in an effort to balance the gradients of concentration
+  and electric potential \cite{donnan_theory_1995}.
 
@@
   place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
-  the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
+  the same result by confining neat monomer between PDMS or glass substrates since 
+  hexagonal mesophases preferentially anchor perpendicular to both surfaces\cite{feng_thin_2016}.
+%  the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
   %MRS8: maybe say what it is, not just what it's named? 
@@
 
-  %BJC6: is this too bold considering the work done at University of Wisconsin?
-  %MRS8: Maybe take out significantly
-  In this study, we achieve a %significantly 
-  more realistic atomistic description of LLC
+  In this study, we achieve a  more realistic atomistic description of LLC
   membranes than, to our knowledge, has ever previously been created, and explore
@@
   information as possible. We are most interested in reproducing the conclusions
-  about structure drawn from small angle X-ray scattering (SAXS)
-  and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
-  conductivity measurements \cite{feng_thin_2016}.
+  about structure drawn from small angle X-ray scattering (SAXS) and wide angle
+  X-ray scattering (WAXS) experiments as well as in matching ionic conductivity
+  measurements \cite{feng_thin_2016}.
 
@@
 
-  In this paper, we perform molecular modeling of the Col\textsubscript{h} assembly 
-  formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
-  phase is a simpler starting point. The system 
-  %MRS8: check rephrasing on this, since we do say later it does have some water
-  %has no water 
-  is not assembled in aqueous phase
-  which allowed us to simulate longer timescales, and there exists detailed experimental
-  characterization of the fully aligned state, including 2D wide-angle X-ray
-  scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
-  structural data. 
+  In this paper, we perform molecular modeling of the Col\textsubscript{h}
+  assembly formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the
+  Col\textsubscript{h} phase is a simpler starting point. The system is not
+  assembled in aqueous phase which allowed us to simulate longer timescales, and
+  there exists detailed experimental characterization of the fully aligned state,
+  including 2D wide-angle X-ray scattering (WAXS) patterns
+  (Figure~\ref{fig:WAXS}) which are useful for reconstructing structural data.
+
   %MRS8: I started tweaking the below, but it might be better just to eliminate.
@@
 
-  Despite having structural data, there is still information which experiment cannot
-  definitively answer. 
-  %MRS8: grammatically a bit redundant.
-  %There are a number of structural questions we wish to answer in this article. 
-  Specifically, we want to know:
+ Despite having structural data, there is still information which experiment
+ cannot definitively answer. Specifically, we want to know:
  \begin{enumerate}
@@
 
-    %MRS7: is this really a liquid crystalline system, even if it is made of liquid crystal monomers? Should we say
-    % in many liquid crystal systems?
-    %BJC5: changed to 'many liquid crystalline systems'
   	We are careful to avoid the term 'layers' since many liquid crystalline systems
@@
 
-	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
-	ambient water are 
-        %leached 
-        absorbed
-        into the system. The hydrogen bonding network formed by the 
-	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
-	to see if there is any meaningful structural difference between a "dry" and a "wet" system.
-
-	\item What is the 
-          %MR8: chemical composition is a bit ambiguous; implies mole fractions, which isn't what we mean
-          %chemical composition 
-          detailed atomistic structure of the pores?\label{point:composition}
+	While the Col\textsubscript{h} phase is described as dry, it is likely
+	that small amounts of ambient water are absorbed into the system. The hydrogen
+	bonding network formed by the water may play a role in structuring the pore. We
+	used simulated X-ray diffraction (XRD) patterns to see if there is any
+	meaningful structural difference between a "dry" and a "wet" system.
+
+	\item What is the detailed atomistic structure of the pores?\label{point:composition}
 
@@
   \subsection{Equilibration}
-  %MRS7: could put this mostly in supporting. 
-  %BJC6: cut in half
-  We developed equilibration schemes for creating dry and wet configurations. Both
-  schemes start with an initial configuration generated according to the previous
-  guidelines. For wet systems, we added the desired concentration of water to 
-  the initial configuration and carried out equilibration in the same way
-  as the dry systems. First, we fixed monomer head groups in place using position
-  restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We gradually
-  released the position restraints by decreasing the force constants over a series
-  of NVT simulations. We allowed the resulting unrestrained structure to equilibrate for
-  5 ns in the NPT ensemble with pressure controlled by the berendsen barostat 
-  followed by NPT equilibration simulations run for at least 400 ns using the 
-  Parrinello-Rahman barostat. 
-  %More precise details are 
-  More equilibration details are 
-  available in 
-  section S-\ref{S-section:equilibration}.
+
+  We developed equilibration schemes for creating dry and wet configurations.
+  Both schemes start with an initial configuration generated according to the
+  previous guidelines. For wet systems, we added the desired concentration of
+  water to the initial configuration and carried out equilibration in the same
+  way as the dry systems. First, we fixed monomer head groups in place using
+  position restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We
+  gradually released the position restraints by decreasing the force constants
+  over a series of NVT simulations. We allowed the resulting unrestrained
+  structure to equilibrate for 5 ns in the NPT ensemble with pressure controlled
+  by the berendsen barostat followed by NPT equilibration simulations run for at
+  least 400 ns using the Parrinello-Rahman barostat. More equilibration details
+  are available in section S-\ref{S-section:equilibration}.
 
@@
 
-  % BJC5: trying things out with 'columns per pore' instead of 'monomers per layer'.
   Our simulations best support a model built with 5 monomer columns per pore based on
@@
   extra space between stacked monomers, monomer head groups have more rotational freedom. We
-  quantified the ordering of the head groups using the nematic order parameter (see section S~\ref{method:nematic_order} for details of calculation). 
-  %MRS8: the reference above isn't appearing. I'm not sure why after quick check.
+  quantified the ordering of the head groups using the nematic order parameter (see section S-\ref{S-method:nematic_order} for details of calculation). 
   Disordered basin systems have a lower nematic order parameter (meaning they are more disordered) 
@@
 
-  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
-  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
-  (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4 columns per pore equilibrate
-  to an average pore spacing 0.25 nm lower than experiment. Ordered basin systems built with
-  6 columns per pore, have an equilibrated pore spacing ca. 0.50 nm higher than experiment.
-  Monomers in disordered basin systems built with 6 columns-per-pore agree with experimental pore-to-pore distances 
-  within error, but stack too far apart. Those in the disordered sandwiched and disordered
-  parallel displaced configurations stack $\sim$4.87 and 4.94 \AA~apart respectively, 
-  which is ca. 1.2~\AA further apart than suggested by experiment. 5 column-per-pore systems
-  stack, at a maximum, 0.9 \AA~further apart than experiment (see Table~\ref{table:correlation_length}). 
-  The remainder of this discussion will focus on the analysis of systems built with 5 columns per pore.
+  Systems built with 5 columns in each pore equilibrate to a pore spacing that
+  is most consistent with the experimental value of 4.12 nm derived from SAXS
+  measurements (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4
+  columns per pore equilibrate to an average pore spacing 0.25 nm lower than
+  experiment. Ordered basin systems built with 6 columns per pore, have an
+  equilibrated pore spacing ca. 0.50 nm higher than experiment.  Monomers in
+  disordered basin systems built with 6 columns-per-pore agree with experimental
+  pore-to-pore distances within error, but stack too far apart. Those in the
+  disordered sandwiched and disordered parallel displaced configurations stack
+  $\sim$4.87 and 4.94 \AA~apart respectively, which is ca. 1.2~\AA further apart
+  than suggested by experiment. 5 column-per-pore systems stack, at a maximum,
+  0.9 \AA~further apart than experiment (see 
+  Table~\ref{table:correlation_length}).  The remainder of this discussion will
+  focus on the analysis of systems built with 5 columns per pore.
 
@@
 
-  To understand the %true 
-  more likely origin of R-spots, we determined which atoms gave rise to the 
-  feature. 
+  To understand the most likely origin of R-spots, we determined which atoms
+  gave rise to the feature. 
   %MRS8: next two sentences repetitive; could you revise? 
-  Since R-spots is present as higher intensity spots within R-alkanes, it is
-  likely that the spots arise as a consequence of the tails. By removing all non-tail atoms
-  from the trajectory and simulating a diffraction pattern with the remaining atoms, we were
-  able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the 
-  tails stay nearly flat, we plotted their centroids (Figure \ref{fig:centroids})
-  and measured the angle between each centroid and its nearest neighbors with respect to the 
-  plane of the membrane. We see distinct peaks in the distribution of these angles 
-  (Figure~\ref{fig:tail_packing}).
+%  Since R-spots is present as higher intensity spots within R-alkanes, it is
+%  likely that the spots arise as a consequence of the tails. 
+  By removing all non-tail atoms from the trajectory and simulating a
+  diffraction pattern with the remaining atoms, we were able to isolate the cause
+  of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the tails stay
+  nearly flat, we plotted their centroids (Figure \ref{fig:centroids}) and
+  measured the angle between each centroid and its nearest neighbors with respect
+  to the plane of the membrane. We see distinct peaks in the distribution of
+  these angles (Figure~\ref{fig:tail_packing}).
 
@@
 
-%BJC6: figures are in order that they are talked about in text.
   \begin{figure}[!htb]
@@
   \end{subfigure}
-  %BJC6: Brought this back to make 6 figures.
   \begin{subfigure}[t]{0.32\linewidth}
@@
   \end{subfigure}
-  %MRS8: nicely organized figure! I think in (c), you do want the red/green dots showing hexagonal symmetry to be bigger; 
-  %when the figure is reduced they are hard to see.
   \caption{(a) R-spots increases in intensity when the temperature of the system is 
@@
 
-  We can also produce R-double if layers are not uniformly spaced. Rather, monomers might form 
-  pairs that stack less than 3.7~\AA~apart, and whose center of masses are spaced 7.4 \AA~ 
-  from the next pair of monomers (Figure ~\ref{fig:staggered_rzplot_norestraints}). To our 
-  knowledge, there have been no studies that specifically address the possibility of a
-  configuration like this. 
-  %MRS8: above: be more precise, for example, QM studies or crystallographic investigation of stacked pi-pi system, 
-  % can cite the reference found.
-  Our force field causes our system to tend towards uniformly spaced
-  layers.   Simulations of unevenly spaced systems are only stable if position restraints
-  are applied to heavy atoms of the phenyl rings.
-  %MRS8: added below.
-  There is little evidence from QM studies of stacked $\pi-\pi$ systems that this behavior is incorrect.~\ref{???}
-
-  Adding water to the system 
-  %facilitates 
-  appears to facilitate 
-  the appearance of R-double,
-  %MRS8: added above.
-I realize the H-bonding isn't brought up until later paragraphs, but I don't want to leave people in suspense; it serves as essentially a thesis of the next few paragraphs, which do group together.
-  through the creation of hydrogen bonding of water to carboxylate groups of consecutive layers.
-  We added water to the 
-  parallel displaced and sandwiched configurations in the ordered basin and equilibrated them
-  according to the wet equilibration procedure. There is no experimental measurement of 
-  water concentration in these membranes so we tested a range of water concentrations from
-  1\% to 5\%. R-double appears transiently in the simulated XRD pattern of the parallel 
-  displaced configuration with 1 wt\% water (Figure \ref{fig:solvated_pore_rzplot_norestraints}). It is
-  not initially present, but appears after 200 ns of simulation time. After 450 ns, it 
-  disappears again. Simulated XRD patterns of all other solvated systems tested are shown 
-  in Figure S~\ref{S-fig:solvation}, however R-double is not present.
+  We can also produce R-double if layers are not uniformly spaced. Rather,
+  monomers might form pairs that stack less than 3.7~\AA~apart, and whose center
+  of masses are spaced 7.4 \AA~ from the next pair of monomers (Figure
+  ~\ref{fig:staggered_rzplot_norestraints}). To our knowledge, there have been no
+  studies that specifically address the possibility of a configuration like this.
+  Our force field causes our system to tend towards uniformly spaced layers.
+  Simulations of unevenly spaced systems are only stable if position restraints
+  are applied to heavy atoms of the phenyl rings.  There is little evidence from
+  QM studies of stacked $\pi-\pi$ systems that this behavior is
+  incorrect.~\ref{tauer_beyond_2005}
+
+  Adding water to the system appears to facilitate the appearance of R-double,
+  through the creation of hydrogen bonding of water to carboxylate groups of
+  consecutive layers. We added water to the parallel displaced and sandwiched
+  configurations in the ordered basin and equilibrated them according to the wet
+  equilibration procedure. There is no experimental measurement of water
+  concentration in these membranes so we tested a range of water concentrations
+  from 1\% to 5\%. R-double appears transiently in the simulated XRD pattern of
+  the parallel displaced configuration with 1 wt\% water (Figure
+  \ref{fig:solvated_pore_rzplot_norestraints}). It is not initially present, but
+  appears after 200 ns of simulation time. After 450 ns, it disappears again.
+  Simulated XRD patterns of all other solvated systems tested are shown in Figure
+  S~\ref{S-fig:solvation}, however R-double is not present.
 
@@
 
-  R-double appears in the solvated system due to the structure of the head groups. To 
-  %prove 
-  demonstrate
-  this,
-  we removed the head groups from the trajectory used to produce Figure~\ref{fig:solvated_pore_rzplot_norestraints}
-  in order to produce that shown in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear
-  without the influence of the head groups. Water molecules must play a role in the structuring
-  of the head groups since R-double does not appear in any dry simulations.
+  R-double appears in the solvated system due to the structure of the head
+  groups. To demonstrate this, we removed the head groups from the trajectory
+  used to produce Figure~\ref{fig:solvated_pore_rzplot_norestraints} in order to
+  produce that shown in Figure~\ref{fig:rdouble_nophenyls}. R-double does not
+  appear without the influence of the head groups. Water molecules must play a
+  role in the structuring of the head groups since R-double does not appear in
+  any dry simulations.
 
@@
   %BJC6: moved this paragraph up to make the section more idea-focused
-  In general, the composition of each region, particularly within our definition of 
-  the pore region, is similar between all systems. 
-  %MRS8: weakened a bit
-  This suggest that the details of transport may be relatively independent of the structural differences between
-  different possible structures studied here.
+  In general, the composition of each region, particularly within our
+  definition of the pore region, is similar between all systems.  This suggests
+  that the details of transport may be relatively independent of the structural
+  differences between different possible structures studied here.
   %We believe we can solvate and study transport
@@
   the collective diffusion model\cite{liu_collective_2013} 
-  (See section S~\ref{s-fig:conductivity}). The values calculated by the 
-  %MRS8: this section reference not working either.
+  (See section S~\ref{S-fig:conductivity}). The values calculated by the 
   collective diffusion model agree with Nernst-Einstein  values within error, 
@@
   counterparts. The correlation length decreases in both systems, 
-  %MRS7: from what to what?
-  %BJC6: If I say that, then shouldn't I say it for all metrics? That sounds
-  % a bit clunky especially when they are plotted in the figure and I just want to make
-  % somewhat general comments on the effect of cross-linking.
   but is most pronounced in the parallel displaced system.
@@
   experiment because monomer stack too far apart. Finally, we observed that our model
-  can only produce
-  %reproduces 
-  R-double when we add 1 wt\% water to the system. This observation has
-  %important 
-  possible
-  implications for the reproducibility of the experimental results from Feng 
-  et al since they claim that their membrane is completely dry.
+  can only produce R-double when we add 1 wt\% water to the system. This observation has
+  possible implications for the reproducibility of the experimental results from Feng 
+  et al. since they claim that their membrane is completely dry.
 
@@
   learned that the pores are generally filled with monomer head groups and sodium
-  ions. All dry systems studied showed a similar distribution of sodium, head groups 
-  and tails while the wet system shows evidence of 
-  %MRS8: modified; water isn't changing things very much.
-  slight
-  swelling, with minor changes in the distributions due to the presence of 
-  water molecules. We also observed that there is not a hard partition between hydrophilic
-  and hydrophobic regions, rather there is a gradient. This finding has raised questions
-  about the nature of size-exclusion separations in systems without a well-defined pore 
-  size, which potentially could give rise to separations that vary with chemical identity as well as size.
+  ions. All dry systems studied showed a similar distribution of sodium, head
+  groups and tails while the wet system shows evidence of slight swelling, with
+  minor changes in the distributions due to the presence of water molecules. We
+  also observed that there is not a hard partition between hydrophilic and
+  hydrophobic regions, rather there is a gradient. This finding has raised
+  questions about the nature of size-exclusion separations in systems without a
+  well-defined pore size, which potentially could give rise to separations that
+  vary with chemical identity as well as size.
 
@@
 
-  %We justified that 
   Our system can reasonably estimate ionic conductivity. Our
@@
   of ca. 1.5, in closer agreement with experiment, the pore spacing decreases and
-  the membrane becomes thicker; 
-  %MRS8: added some.
-  however, all changes are relatively minor, preserving most of the features well.
+  the membrane becomes thicker; however, all changes are relatively minor, 
+  preserving most of the features well.
 
@@
 
-  %MRS8: better to rephrase what can be done (which is a present thing) instead of what we will do (which is future and undetermined).
-  With the structural understanding gained by these simulations, 
-  %we will
-  it becomes possible
-  evaluate transport of various solutes within the system, and apply the
+  With the structural understanding gained by these simulations, it becomes
+  possible evaluate transport of various solutes within the system, and apply the
   knowledge gained from this study in order to suggest improvements to the

### 2018-06-18 Ben_Manuscripts/structure_paper/Draft.tex
Figure updates

@@
 
-% BJC5 : This is how it is described in Xunda's papers. Should I shift to something
-% that doesn't rely on stacked disks? Maybe illustrate monomers stacked into
-% columns instead?
-% BJC6 : I will get to redo-ing this. Just takes some time to refamiliarize myself with
-% the software I used to create it
-%MRS8: sound good.
   \begin{figure}
@@
 		\centering
-		\includegraphics[width=\textwidth]{layer_thick.png}
+		\includegraphics[width=\textwidth]{columns.png}
 		\caption{}~\label{fig:wedge_layer}
@@
 	\end{subfigure}
-	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
-	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
-	hydrophilic head groups (blue) facing towards the disk center. The disks
-	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
+	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
+	exhibits wedge-like character. (d) Monomers stack on top of each other with
+	short range order and assemble into pores. (e) The hydrophilic head groups 
+	(blue) facing towards the pore center. The pores assemble into hexagonally
+	packed columnar mesophases.}~\label{fig:assembly}
   \end{figure}
@@
         \centering
-        \begin{subfigure}[t]{0.43\linewidth}
+        \begin{subfigure}[t]{0.405\linewidth}
                 \centering
@@
         \end{subfigure}
-        \begin{subfigure}[t]{0.47\linewidth}
+        \begin{subfigure}[t]{0.495\linewidth}
                 \centering
@@
   configuration from the trajectory which we used for full system
-  construction (Figure~\ref{fig:python}a). See section S-\ref{S-section:parameterization} 
+  construction (Figure~\ref{fig:build_procedure}a). See section S-\ref{S-section:parameterization} 
   for further detail of the parameterization process.
@@
   into a structure close to one of a number of hypothesized equilibrium configurations
-  (Figure~\ref{fig:python}).
+  (Figure~\ref{fig:build_procedure}).
 
   % BJC5: This needs to be modified to reflect columnar build procedure
-  \begin{figure}
-	\centering
-	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}[t]{0.45\textwidth}
+  \includegraphics[width=\linewidth]{monomer_diagonal.png}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.42\textwidth}
+  \includegraphics[width=\linewidth]{stacked_monomers.png}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.35\textwidth}
+  \includegraphics[width=\linewidth]{initial_pore.png}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.45\textwidth}
+  \includegraphics[width=\linewidth]{initial_unit_cell.png}
+  \caption{}
+  \end{subfigure}
   \caption{(a) We parameterized a single monomer and annealed it to produce a low energy
-		configuration. (b) A Python script assembles monomers into columns which are duplicated 
-		and rotated to surround hydrophilic pore centers. (c) We chose to stack twenty monomers
-		into each column. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
+		configuration. (b) We assembled monomers into columns by stacking them on top of each 
+		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
+		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
+		placed them into a monoclinic unit cell.}\label{fig:build_procedure}
   \end{figure}
+
+  %BJC7: old
+%  \begin{figure}
+%	\centering
+%	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
+%	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
+%		configuration. (b) A Python script assembles monomers into columns which are duplicated 
+%		and rotated to surround hydrophilic pore centers. (c) We chose to stack twenty monomers
+%		into each column. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
+%  \end{figure}
 
@@
   measured ion concentration with respect to the volume of the entire unit cell. 
-  More details are provided in the Supporting Information, Section~S-\ref{section:ionic_conductivity}.
+  More details are provided in the Supporting Information, Section~S-\ref{S-section:ionic_conductivity}.
 

### 2018-07-05 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex
Fourier transform of variations on a simple syste

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{hyperref}
\title{Simulated Structure Factors}
\author{Benjamin J. Coscia}
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle

  \section{Calculation of the structure factor}

  The structure factor, S($\mathbf{q}$), relates the observed intensity per
  atom to that observed by a single scattering unit. Incident plane waves falling
  on a material have a wave vector, $K_i$, whose length is
  $\dfrac{2\pi}{\lambda}$, where $\lambda$ is the wavelength. The diffracted wave
  vector, $K_f$, has the same length as $K_i$ if the diffraction process is 
  elastic. We will assume elasticity going forward. The scattering vector, $\mathbf{q}$
  is defined as $K_f - K_i$. Since $K_f$ and $K_i$ are the same length, the scattering
  vector must lie on the surface of a sphere of radius $\dfrac{2\pi}{\lambda}$. This
  sphere is called the Ewald Sphere and diffraction will only occur for reciprocal
  lattice points that lie on its surface.

  The amplitude and phase of the scattered waves is the vector sum of all scattered 
  waves from all atoms:
  \begin{equation}
  \Psi_s(\mathbf{q}) = \sum_{j=1}^{N}f_je^{-i\mathbf{q}\boldsymbol{\cdot}\mathbf{R_j}}\label{eqn:dft}
  \end{equation}
  where $f_j$ is the atomic form factor of atom $j$ and $\mathbf{R_j}$ is the position of
  the atom in real space. Note that Equation \ref{eqn:dft} is the definition of the 
  discrete fourier transform.

  The scattered intensity is obtained by multiplying Equation \ref{eqn:dft} by its 
  complex conjugate:
  \begin{equation}
  I(\mathbf{q}) = \Psi_s(\mathbf{q})\cdot\overline{\Psi_s}(\mathbf{q}) = \sum_{j=1}^{N}f_je^{-i\mathbf{q}\boldsymbol{\cdot}\mathbf{R_j}} \times \sum_{k=1}^{N}f_ke^{-i\mathbf{q}\boldsymbol{\cdot}\mathbf{R_k}} = \sum_{j=1}^{N}\sum_{j=k}^{N}f_jf_ke^{-i\mathbf{q}\boldsymbol{\cdot}(\mathbf{R_j}- \mathbf{R_k})}
  \label{eqn:conjugate}
  \end{equation}
  Computationally, one should calculate the fourier transform of the atomic
  coordinates with a fast fourier transform, calculate its complex conjugate and 
  multiply them together. The structure factor is typically normalized as 
  $ 1 / {\sum_{j=1}^{N} {f_j}^2}$ so that it is independent of system size, and
  the general equation for the structure factor becomes:
  \begin{equation}
  S(\mathbf{q})= \dfrac{1}{\sum_{j=1}^{N} {f_j}^2}\sum_{j=1}^{N}\sum_{j=k}^{N}f_jf_ke^{-i\mathbf{q}\boldsymbol{\cdot}(\mathbf{R_j}- \mathbf{R_k})}
  \label{eqn:general_sf}
  \end{equation}

  If all atoms are identical, equation \ref{eqn:general_sf} simplifies to:
  \begin{equation}
  S(\mathbf{q})= \dfrac{1}{N}\sum_{j=1}^{N}\sum_{j=k}^{N}e^{-i\mathbf{q}\boldsymbol{\cdot}(\mathbf{R_j}- \mathbf{R_k})}
  \label{eqn:simplified_sf}
  \end{equation}

  The atomic form factor, $f_j$ is more complicated than how it is represented
  in Equation \ref{eqn:dft}. The atomic form factor is the scattering
  contribution from a single isolated atom. They are calculated as the fourier
  transform of the electron density, $\rho({\mathbf{r}})$,  which is typically
  calculated using quantum techniques. Since $\rho({\mathbf{r}})$ is a spatially
  dependent function, $f_j$ is actually a function of $\mathbf{q}$,
  $f(\mathbf{q})$. Values of $f(\mathbf{q})$ for each element are tabulated in
  the \href{http://it.iucr.org/Cb/ch6o1v0001/}{International Tables for
  Crystallography}. For $\mathbf{q}=\mathbf{0}$, the atomic form factor is equal to the 
  number of electrons possessed by the atom.

  The resolution in each dimension of reciprocal space is determined by the
  size of the unit cell studied. In order to calculate the structure factor, the
  system's 3D coordinates must be discretized into regularly sampled points using
  a histogramming method. Applying equation~\ref{eqn:general_sf} to the histogram
  will yield a grid with Fourier bin sizes of $\dfrac{2\pi}{L_i}$ (i = (x,y,z)).
  The fourier transform of an array of values returns a same length array of
  frequencies. Increasing the number of bins in the histogram will not change the
  size of the Fourier space bins, rather it will increase the maximum accessible
  value of $q$.

  \section{Structure factor of hexagonally packed columns}

  Here, we explore, in depth, a simplified model of an inverted hexagonal phase
  lyotropic liquid crystal (H\textsubscript{II} LLC). The simplified model is
  meant to enhance our understanding of the structure factor of a fully atomistic
  model of the same material. We are primarily interested in the diffraction
  patterns produced by the head groups so we model each monomer as a point placed
  at the center of mass of its head group. The hexagonal phase is made up
  straight pore columns. Each pore column is composed of columns of stacked
  monomers which surround the pore's hydrophilic core. Based on simulation, there
  are likely 5 monomer columns making up each pore, and the pore radius is ca. 1
  nm. Experimental WAXS suggests that monomers stack 3.7 \AA apart, and SAXS
  measurements have shown that pores are spaced ca. 4.1 nm apart. Here we took the 
  pore spacing to be 4.25 nm for no good reason. For consistency with simulation,
  we will look at 4 pores in a monoclinic unit cell with 5 monomer columns per pore.

  We are interested in the intensity and dimensions of the R-$\pi$ reflection,
  which is a consequence of monomers stacked on top of each other in the
  z-direction.

  \subsection{Crystalline liquid crystals}

  For a perfect, infinite crystal, the intensity of R-$\pi$ is infinitely sharp. We
  created a model with perfectly aligned columns. Each columns originates at z=0
  and all other points in the column are equally spaced 3.7 \AA apart in the
  z-direction (Figure~\ref{fig:perfect_crystal_xyz}). This essentially creates
  layers of atoms. The intensity of R-$\pi$ for systems of various size are shown
  in Table~\ref{table:perfect_size_dependence}. The intensity of R-$\pi$ is equal
  to the number of atoms in the unit cell. The intensity will approach infinity as
  the system size increases.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{perfect_crystal_xyz.png}
  \caption{}\label{fig:perfect_crystal_xyz}
  \end{figure}

  \begin{table}
  \centering
  \begin{tabular}{c c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores &  Number of Atoms & R-$\pi$ Intensity & FWHM ($\AA^{-1}$) \\
  \midrule
  14.8        &      4            &       4          & 80               & 80               & 0.34  \\
  18.5        &      5            &       4          & 100              & 100              & 0.34  \\
  37          &      10           &       4          & 200              & 200              & 0.34  \\
  14.8        &      4            &       9          & 180              & 180              & 0.36  \\
  18.5        &      5            &       9          & 225              & 225              & 0.36  \\
  37          &      10           &       9          & 450              & 450              & 0.36  \\
  14.8        &      4            &       16         & 320              & 320              & 0.43  \\
  18.5        &      5            &       16         & 400              & 400              & 0.43  \\
  37          &      10           &       16         & 800              & 800              & 0.43  \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ in a perfect crystal is equal to the number of
  scatterers in the unit cell.}\label{table:perfect_size_dependence}
  \end{table}

  We measured the peak width of R-$\pi$ in the $q_r$ direction using the
  appropriate slice of the structure factor. Ideally, one should use the angle
  averaged structure factor for this calculation, but since the angle averaging
  procedure interpolates between bins, the averaged intensities are lower than
  expected which slightly changes the shape of the peak. This reflection is
  radially symmetric about the z-axis, so we fit peak widths to cross-sections at
  (0, y, 1.7)$^{-1}$ \AA.

  The distance, d, between peaks in the $q_y$ cross-sections of the structure
  factor is equal to $2\pi / d$ (Figure~\ref{fig:p2p_rpi}). We looked at systems
  with pores spaced 42.5 nm and 212.5 nm apart respectively.  The fundamental
  frequency appears where expected, based on d. Subharmonics follow the
  fundamental frequency at equally spaced intervals of width $2\pi / d$.

  \begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{constant_p2p.png}
  \includegraphics[width=0.45\textwidth]{constant_npores.png}
  \caption{The distance between peaks of the structure factor cross-section at
  (0, y, 1.7) is equal to the distance between pores in q-space. The first off-center
  peak of each distribution shows the fundamental frequency. The peaks that follow at 
  higher |$\mathbf{q}$| values are subharmonics. Both systems shown are in unit cells 
  with dimensions of 42.5 x 42.5 x 3.7 nm. (a) The pore-to-pore spacing was held at 
  42.5 nm. The unit cell consists of 100 total pores. The first peak is located at 
  $q_y = .148 \AA^{-1}$ which corresponds to $2\pi / .148 = 42.5 \AA$ in real space. (b)
  We placed four pores in a unit cell spaced 21.25 nm apart. The first peak appears where
  expected at $q_y = 0.0296 \AA^{-1}$ and all other peaks are separated by the same distance.
  }\label{fig:p2p_rpi}
  \end{figure}

  We quantified the peak width by fitting gaussian curves to the R-$\pi$ peak
  cross-sections and measuring ther full width at half maximum. Gaussian profiles
  appear to give the closest fit to the data (see Figure~\ref{fig:fwhm_fits}). We
  calculated all of FWHMs in ~\ref{table:perfect_size_dependence} using gaussian
  fits.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fwhm_fits.png}
  \caption{The gaussian functional form more closely matches the data than the Lorentzian
  functional form. Shown is data for a perfect crystal system with 4 pores and 4 points
  per column.}\label{fig:fwhm_fits}
  \end{figure}

  The distance between pores does not affect the FWHM of the R-$\pi$ peak in
  the $q_y$ direction.  We held the size of the unit cell constant at 42.5 x 42.5
  x 3.7 nm and varied the number of pores (and consequently, the distance between
  pores). We generated error bars for the fits based on the covariance of the
  optimized fit parameters. There is no statistical difference between the
  calculated values of each FWHM. The uncertainty is lower for systems with less
  pores since there are more subharmonics available for curve fitting. The values
  of FWHM in Table~\ref{fig:perfect_size_dependence} are calculated using model
  systems with 4 pores and the same box dimensions used here.

  \begin{table}
  \centering
  \begin{tabular}{c c c c c}
  \toprule
  $L_z$ (\AA) & Number of Pores & Distance between Pores &  R-$\pi$ intensity & FWHM ($\AA^{-1}$) \\
  \midrule
  37          &      4            & 212.5                & 200                & 0.372 $\pm$ 0.004 \\ 
  37          &      25           & 85.0                 & 1250               & 0.371 $\pm$ 0.008 \\
  37          &      100          & 42.50                & 5000               & 0.375 $\pm$ 0.013 \\
  \bottomrule
  \end{tabular}
  \caption{We held the size of the unit cell constant at 42.5 x 42.5 x 3.7 nm and varied the
   number of pores and distance between pores. The value of FWHM is indistinguishable between
   the systems.}\label{table:randomly_displaced_columns}
  \end{table}

  The finite FWHM of perfectly crystalline systems is due to non-uniform
  ordering of the columns within the pores. Although all scatterers are aligned
  and equally spaced in the z-direction, the individual columns of scatterers are
  offset from the pore center. Therefore, there is a range of similar but
  different distances between scatter scatterers. There are many opportunities
  for constructive and destructive interference with wavelengths slightly
  different than those which contribute to the fundamental frequency. If we place
  only one column at each pore center, the FWHM becomes infinite (See
  Figure~\ref{fig:infinite_FWHM})

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{one_column_per_pore.png}
  \caption{We placed one column of scatterers at each of 4 pore centers, spaced apart by
  212.5 nm. Since the y-component of the distance between all scatteres is the same in 
  all cases, subharmonics appear just as strongly as the fundamental frequency. Since the 
  intensity doesn't decay, the FWHM is infinite.}\label{fig:infinite_FWHM}
  \end{figure}

  % peaks may artifically broaden upon angle-averaging.

  The real system is far from a perfect crystal. Here we explore the influence
  of 3 sources of disorder on the intensity of R-$\pi$:
  \begin{enumerate}
  \item Random z-displacement of columns with respect to all other columns
  \item Random rotation of layers about the z-axis
  \item Thermal noise
  \end{enumerate}

  \subsection{Imperfectly aligned columns}

  We randomly aligned columns along the z-axis by adding a random displacement
  to each column of points. This simulates a system in which columns are
  uncorrelated.  We shifted coordinates where necessary so that all atoms stayed
  within the unit cell. We held the spacing between each point within each column
  remained at exactly 3.7 \AA. We created  trajectories of 1000 independent
  configurations in order to calculate the average intensity of R-$\pi$. 1000
  independent configurations gives a reasonably converged average, enough to
  observe trends.

  The intensity of R-$\pi$ is equal to the number of scatterers per
  column when we randomly displace columns with respect to each other (See
  Table~\ref{fig:randomly_displaced_columns}).  It is independent of the
  number of pores (and hence number of columns) in the system. The error 
  in the calculated intensities are comparable to the magnitude of the 
  intensity because the intensity of each configuration in the trajectory
  fluctuates so much.

  \begin{table}
  \centering
  \begin{tabular}{c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores &  R-$\pi$ Intensity\\ 
  \midrule
  14.8        &      4            & 4               & 3.98              \\
  18.5        &      5            & 4               & 5.05              \\
  37          &      10           & 4               & 10.08             \\
  14.8        &      4            & 9               & 4.06              \\
  18.5        &      5            & 9               & 4.78              \\
  37          &      10           & 9               & 10.19             \\
  14.8        &      4            & 16              & 4.01              \\
  18.5        &      5            & 16              & 4.95              \\
  37          &      10           & 16              & 9.61              \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in 
   each column when columns are uncorrelated.}\label{table:randomly_displaced_columns}
  \end{table}

  The $q_y$ width of R-$\pi$ is infinite when columns are randomly displaced in
  the z-direction. We attempted to measure the FWHM of the system with randomly
  displaced columns containing 4 pores and $L_z = 37$. The cross-section
  (Figure~\ref{fig:random_columns_qy}) shows non-decaying noise centered near 10,
  the same R-$\pi$ intensity in Table~\ref{table:randomly_displaced_columns}. The 
  angle averaged pattern (Figure~\ref{fig:random_columns_rzplot}) further illustrates
  the diffraction lines which characterize this type of system.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_qy.png}
  \caption{}\label{fig:random_columns_qy}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_rzplot.png}
  \caption{}\label{fig:random_columns_rzplot}
  \end{subfigure}
  \caption{}\label{fig:random_columns_rpi_width}
  \end{figure}

  \subsection{Randomly rotated layers}

  We observed the influence of correlation between layers by randomly rotating layers
  of scatterers about the z-axis. We held constant the angle, with respect to the pore
  center, between scatterers for any given layer. For examples, since there are 5 
  columns per pore, each layer is made of 5 monomers. The angle made between the two 
  vectors extending from the pore center to two adajacent scatterers in a single layer
  is 72 $\degree$ with respect to the xy plane.

  \begin{table}
  \centering
  \begin{tabular}{c c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores & Number of Atoms & R-$\pi$ Intensity & FWHM $\AA^{-1}$ \\
  \midrule
  14.8        &      4            & 4               & 80              &  80               & 0.37           \\
  18.5        &      5            & 4               & 100             &  100              & 0.37           \\
  37          &      10           & 4               & 200             &  200              & 0.37           \\
  14.8        &      4            & 9               & 180             &  180              & 0.37           \\
  18.5        &      5            & 9               & 225             &  225              & 0.37           \\
  37          &      10           & 9               & 450             &  450              & 0.37           \\
  14.8        &      4            & 16              & 320             &  320              & 0.37           \\
  18.5        &      5            & 16              & 400             &  400              & 0.37           \\
  37          &      10           & 16              & 800             &  800              & 0.37           \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in
   each column when columns are uncorrelated. Note that reproducing these results requires a very fine histogram, 
   and thus a much more expensive calculation. The default binning scheme (100 bins in each dimension) gives slightly
   misleading answers.}\label{table:randomly_displaced_columns}
  \end{table}

  The max intensity of R-$\pi$ and the FWHM of the $q_y$ structure factor
  cross-section at R-$\pi$ are exactly the same as those of the perfect crystal.

  \subsection{Influence of noise}

  \subsection{Influence of Pore Radius}

\end{document}

### 2018-07-05 Ben_Manuscripts/fourier_transforms/Outline.tex
Fourier transform of variations on a simple syste

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\title{Intuitive explanations of X-ray diffraction patterns}
\author{Benjamin J. Coscia \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle

  \section{Topics to explore}

  Topics here are trivial to people who have long been immersed in crystallography or a related field. This stuff is far from intuitive

  Reference Atlas of optical transforms
  \begin{itemize}
  	\item 2D transforms of 2D arrays explored in detail
	\item Here we look at slices of 3D transforms created from 3D coordinates
  \end{itemize}

  \begin{itemize}
	\item Narrow to structures with periodic order (eliminate proteins, amporphous materials)
	\item Will not talk about instrumentation
	\item Common crystal lattices
	\begin{itemize}
		\item 1D and 2D patterns (potentially 3D)
		\item Perfect lattices
		\item Sample orientation 
		\item Add noise in each dimension
	\end{itemize}
	\item Common liquid crystal phases
	\begin{itemize}
		\item show 1D and 2D patterns
		\item Nematic
		\item Columnar
		\item Bicontinuous Cubic
		\item Smectic
	\end{itemize}
	\item Other shapes
	\begin{itemize}
		\item helices + screw axes
	\end{itemize}			
	\item Effect of tortuosity
	\item Effect of misaligned domains - angle averagin
	\item Intensity of subharmonics

\end{document}

### 2018-07-09 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex
FT updates + newish figures for poster

@@
 
-  \begin{table}
+  \begin{table}[!htb]
   \centering
@@
 
-  \subsection{Influence of noise}
-
   \subsection{Influence of Pore Radius}
 
+  The pore radius is inversely proportional to the FWHM of systems made with
+  randomly rotated layers (See Figure~\ref{fig:pore_radius}). This result is
+  not extremely surprsing, although the limits of the relationship suggest 
+  that a pore radius of 0 should give an infinite FWHM (supported by Figure
+  ~\ref{fig:infinite_FWHM}) and an infinitely large pore radius should have 
+  a zero FWHM. This result is also interesting because it suggests that one
+  can measure relative pore radii using X-ray diffraction. The difficulty,
+  which is associated with the phase problem, is deconvoluting the electron
+  density associated with just pore entities.
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{pore_radius_FWHM.png}
+  \caption{The FWHM decays with increasing pore radius.}\label{fig:pore_radius}
+  \end{figure}
+
+%  \begin{table}
+%  \centering
+%  \begin{tabular}{c c c c c c}
+%  \toprule
+%  $L_z$ (\AA) &   Pore Radius ($\AA^{-1}$) & FWHM ($\AA^{-1}$)  \\
+%  \midrule
+%  37          &      1                     &     1.770          \\
+%  37          &      2                     &     0.999          \\
+%  37          &      3                     &     0.642          \\
+%  37          &      4                     &     0.465          \\
+%  37          &      5                     &     0.372          \\
+%  37          &      7	                   &     0.264          \\
+%  37          &      10                    &     0.186          \\
+%  37          &      15                    &     0.123          \\
+%  \bottomrule
+%  \end{tabular}
+%  \caption{All systems contain four pores with 5 columns per pore and a unit cell
+%  size of 42.5x42.5x3.7 nm. 
+%  }\label{table:pore_radius}
+%  \end{table}
+
+  \subsection{The influence of thermal disorder}
+
+  We added gaussian noise in each dimension to observe its influence on the intensity
+  of R-$\pi$ and the FWHM. For the z-direction, the standard deviation of the 
+  gaussian distribution is equal to a fraction of the average distance between scatterers
+  in columns. In the xy-directions, the standard deviation is equal to a fraction 
+  of the pore radius.
+
+  \subsubsection{Randomly displaced columns}
+
+  When we add noise in the z direction, the intensity of R-$\pi$ decays while the
+  FWHM remains infinite.
+
+  When we add noise in the x and y directions, R-$\pi$ has a finite peak width in its 
+  $q_y$ dimension. We fit a Gaussian function to the
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{random_columns_gaussian.png}
+  \caption{}\label{fig:FWHM_columns}
+  \end{figure}
+
 \end{document}

### 2018-07-10 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex
Pics for poster

@@
   The real system is far from a perfect crystal. Here we explore the influence
-  of 3 sources of disorder on the intensity of R-$\pi$:
+  of 4 sources of disorder on the intensity of R-$\pi$:
   \begin{enumerate}
@@
   \item Thermal noise
+  \item Finite correlation between scatterers in the z-direction
   \end{enumerate}
@@
   When we add noise in the x and y directions, R-$\pi$ has a finite peak width in its 
-  $q_y$ dimension. We fit a Gaussian function to the
+  $q_y$ dimension, and the intensity stays constant. We fit a Gaussian function to the 
+  the $q_y$ cross-section in order to determine its FWHM. The FWHM decay is inversely
+  proportional to the amount of noise added.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{random_columns_z_noise.png}
+  \caption{}\label{fig:z_noise_columns}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{random_columns_gaussian.png}
+  \caption{}\label{fig:FWHM_fit_columns}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{random_columns_xy_noise.png}
+  \caption{}\label{fig:FWHM_columns}
+  \end{subfigure}
+  \caption{(a) The intensity of R-$\pi$ decays to 1 rapidly as gaussian noise is 
+   added to the system. (b) When we add noise in the x and y directions, R-$\pi$
+   broaden in the y-direction with a continuous intensity distribution that can be
+   fit to a gaussian. (c) This FWHM decreases as the inverse of the amount of 
+   noise added.}\label{fig:columns_noise}
+  \end{figure}
+
+  \subsubsection{Randomly rotated layers}
+
+  When we add noise in the z direction, the intensity of R-$\pi$ decays to 1
+  rapidly (Figure~\ref{fig:random_layers_z_noise}), much like the decay shown in
+  Figure ~\ref{fig:z_noise_columns}. The FWHM slowly increases until it jumps to
+  infinity when the intensity of R-$\pi$ is comparable to the background
+  intensity.
+
+  When we add noise in the x and y directions, the intensity of R-$\pi$ does not change.
+  The FWHM slowly decays as shown in Figure~\ref{fig:random_layers_xy_noise}
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{random_columns_gaussian.png}
-  \caption{}\label{fig:FWHM_columns}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{random_layers_z_noise.png}
+  \caption{}\label{fig:random_layers_z_noise}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{random_layers_xy_noise.png}
+  \caption{}\label{fig:random_layers_xy_noise}
+  \end{subfigure}
+  \caption{(a) As we add noise in the z-direction, the intensity of R-$\pi$ decreases
+   rapidly to 1. The FWHM goes to infinity when the intensity of R-$\pi$ equals 1.}\label{fig:layers_noise}
   \end{figure}
 
+  \subsection{Finite z-correlations}
+
+  The z-cross-section of the R-$\pi$ peaks are delta functions in all of the
+  above systems (See Figure~\ref{fig:deltas}). None of the routes explored so far
+  show how R-$\pi$ might broaden. The delta-function behavior does not change
+  when the system is made taller so as to increase the resolution in z. We built
+  a system 10x taller (37 nm), added random column displacement and some noise in
+  the z-direction. R-$\pi$ is still a sharp delta function
+  (Figure~\ref{fig:tall_rpi}).
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{perfect_rpi.png}
+  \caption{Perfect Crystal}\label{fig:perfect_rpi}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{displace_columns_rpi.png}
+  \caption{Randomly displaced columns}\label{fig:displaced_columns_rpi}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{displaced_columns_z_noise_rpi.png}
+  \caption{Randomly displaced columns w/ z-noise}\label{fig:displaced_columns_z_noise_rpi}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{rotated_layers_rpi_xy_noise.png}
+  \caption{Randomly rotated layers w/ xy-noise}\label{fig:rotated_layers_rpi_xy_noise}
+  \end{subfigure}
+  \caption{Several examples of the delta-like behavior of R-$\pi$. Randomly displacing
+  columns, randomly rotating layers, and adding thermal disorder do not broaden 
+  the z-cross-section of R-$\pi$.}\label{fig:deltas}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{tall_rpi.png}
+  \caption{R-$\pi$ still appears to be a delta function even with higher resolution and
+  noise in the z-positions of the scatterers}
+  \end{figure}
+
+  (Please let me know if there is a more correct way of doing this)
+  We added a correlation length to scatterers in z-direction. To do so, we
+  define a covariance matrix to describe the correlation between all pairs of
+  scatterers.  The variance, v, is defined so that the covariance in position of
+  a scatterer with itself is the same for all scatterers. The covariance in
+  position between scatterers decays exponentially from v according to the
+  equation $ve^{-z/L}$ where L is the correlation length. Note that in its
+  current implementation, it does not take periodicity into account, so a
+  correlation length shorter than the box is necessary. A visualization of a
+  typical covariance matrix for a column containing 20 scatterers is shown in
+  Figure~\ref{fig:covariance}. Next, we drew random sample from a multivariate
+  normal distribution defined using the covariance matrix.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{covariance.png}
+  \caption{}\label{fig:covariance}
+  \end{figure}
+
+  Adding a finite correlation length between scatterers causes R-$\pi$ to
+  broaden. We simulated a system with dimensions of 8.5 x 8.5 x 37 nm, so that
+  there would be 100 scatterers in the z-direction and a fourier bin size of
+  $1/370=0.0027 \\A^{-1}$.
+
 \end{document}

### 2018-07-10 analysis/regional_density.py

@@ -76,6 +76,8 @@ if __name__ == "__main__":
         colors = ['xkcd:blue', 'xkcd:olive', 'xkcd:orangered', 'xkcd:magenta', 'xkcd:gold']
         names = ['Ordered Parallel Displaced', 'Ordered Sandwiched', 'Disordered Sandwiched',
                  'Disordered Parallel Displaced', 'Solvated Parallel Displaced']
+        names = ['Parallel Displaced (d=3.7)', 'Sandwiched (d=3.7)', 'Sandwiched (d=5.0)', 'Parallel Displaced (d=5.0)',
+                 'Solvated Parallel Displaced']
         # names = ['Dry', 'Solvated']
         # colors = ['xkcd:orange', 'xkcd:blue', 'xkcd:orange']
 
@@ -100,7 +102,7 @@ if __name__ == "__main__":
 
         outline = np.zeros([4, n, r.shape[0]*2 + 2, 2])
         for i in range(len(regions)):
-            plt.figure(i)
+            fig = plt.figure(i)
             for j in range(n):
                 #plt.bar(r, results[j, i, :], bin_width, color=colors[j], alpha=1, label=names[j])
 
@@ -118,9 +120,11 @@ if __name__ == "__main__":
                     plt.plot(outline[i, j, 1:, 0], outline[i, j, 1:, 1], color=colors[j], linewidth=2,
                              label=names[j])
             # plt.title(regions[i], fontsize=14)
-            plt.legend(fontsize=11)
-            plt.ylabel('Component Number Density (number/nm$^3$)', fontsize=14)
-            plt.xlabel('Distance from pore center, r (nm)', fontsize=14)
+
+            plt.legend(fontsize=18)
+
+            plt.ylabel('Component Number Density \n (number/nm$^3$)', fontsize=18)
+            plt.xlabel('Distance from pore center, r (nm)', fontsize=18)
             plt.axes().tick_params(labelsize=14)
             # plt.ylim([0, 0.6])
             plt.tight_layout()

### 2018-07-10 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex
Edits to fourier transform document

@@
 \usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
+\usepackage{amsmath,amssymb} 
 \usepackage{siunitx}
@@
 \begin{document}
-  \bibliographystyle{ieeetr}
   \graphicspath{{./figures/}}
@@
   vector, $K_f$, has the same length as $K_i$ if the diffraction process is 
-  elastic. We will assume elasticity going forward. The scattering vector, $\mathbf{q}$
+  elastic. We will assume elasticity going forward. The scattering vector, $\mathbf{q}$,
   is defined as $K_f - K_i$. Since $K_f$ and $K_i$ are the same length, the scattering
@@
   waves from all atoms:
-  \begin{equation}
-  \Psi_s(\mathbf{q}) = \sum_{j=1}^{N}f_je^{-i\mathbf{q}\boldsymbol{\cdot}\mathbf{R_j}}\label{eqn:dft}
+
+  \begin{equation}\label{eq:dft}
+  \Psi_s(\mathbf{q}) = \sum_{j=1}^{N}f_je^{-i\mathbf{q}\boldsymbol{\cdot}\mathbf{R_j}}
   \end{equation}
+
   where $f_j$ is the atomic form factor of atom $j$ and $\mathbf{R_j}$ is the position of
-  the atom in real space. Note that Equation \ref{eqn:dft} is the definition of the 
-  discrete fourier transform.
+  the atom in real space. Note that Equation 1 %\eqref{eq:dft} %equation reference not working for some reason
+  is the definition of the discrete fourier transform.
 
-  The scattered intensity is obtained by multiplying Equation \ref{eqn:dft} by its 
-  complex conjugate:
-  \begin{equation}
+  The scattered intensity is obtained by multiplying Equation 1%\eqref{eq:dft} 
+  by its complex conjugate:
+  \begin{equation}\label{eqn:conjugate}
   I(\mathbf{q}) = \Psi_s(\mathbf{q})\cdot\overline{\Psi_s}(\mathbf{q}) = \sum_{j=1}^{N}f_je^{-i\mathbf{q}\boldsymbol{\cdot}\mathbf{R_j}} \times \sum_{k=1}^{N}f_ke^{-i\mathbf{q}\boldsymbol{\cdot}\mathbf{R_k}} = \sum_{j=1}^{N}\sum_{j=k}^{N}f_jf_ke^{-i\mathbf{q}\boldsymbol{\cdot}(\mathbf{R_j}- \mathbf{R_k})}
-  \label{eqn:conjugate}
   \end{equation}
@@
   the general equation for the structure factor becomes:
-  \begin{equation}
+  \begin{equation}\label{eqn:general_sf}
   S(\mathbf{q})= \dfrac{1}{\sum_{j=1}^{N} {f_j}^2}\sum_{j=1}^{N}\sum_{j=k}^{N}f_jf_ke^{-i\mathbf{q}\boldsymbol{\cdot}(\mathbf{R_j}- \mathbf{R_k})}
-  \label{eqn:general_sf}
   \end{equation}
 
-  If all atoms are identical, equation \ref{eqn:general_sf} simplifies to:
-  \begin{equation}
+  If all atoms are identical, Equation 2 %\ref{eqn:general_sf} 
+  simplifies to:
+  \begin{equation}\label{eqn:simplified_sf}
   S(\mathbf{q})= \dfrac{1}{N}\sum_{j=1}^{N}\sum_{j=k}^{N}e^{-i\mathbf{q}\boldsymbol{\cdot}(\mathbf{R_j}- \mathbf{R_k})}
-  \label{eqn:simplified_sf}
   \end{equation}
@@
   The atomic form factor, $f_j$ is more complicated than how it is represented
-  in Equation \ref{eqn:dft}. The atomic form factor is the scattering
+  in Equation 1 %\ref{eqn:dft}. 
+  The atomic form factor is the scattering
   contribution from a single isolated atom. They are calculated as the fourier
@@
   system's 3D coordinates must be discretized into regularly sampled points using
-  a histogramming method. Applying equation~\ref{eqn:general_sf} to the histogram
+  a histogramming method. Applying equation 2 %~\ref{eqn:general_sf}
+  to the histogram
   will yield a grid with Fourier bin sizes of $\dfrac{2\pi}{L_i}$ (i = (x,y,z)).
@@
   patterns produced by the head groups so we model each monomer as a point placed
-  at the center of mass of its head group. The hexagonal phase is made up
+  at the center of mass of its head group. The hexagonal phase is made of
   straight pore columns. Each pore column is composed of columns of stacked
@@
   nm. Experimental WAXS suggests that monomers stack 3.7 \AA apart, and SAXS
-  measurements have shown that pores are spaced ca. 4.1 nm apart. Here we took the 
-  pore spacing to be 4.25 nm for no good reason. For consistency with simulation,
-  we will look at 4 pores in a monoclinic unit cell with 5 monomer columns per pore.
+  measurements have shown that pores are spaced ca. 4.1 nm apart. Here, unless
+  otherwise noted we took the pore spacing to be 4.25 nm for no good reason. For
+  consistency with simulation, we will look at 4 pores in a monoclinic unit cell
+  with 5 monomer columns per pore, unless specified otherwise.
 
@@
   created a model with perfectly aligned columns. Each columns originates at z=0
-  and all other points in the column are equally spaced 3.7 \AA apart in the
+  and all other points in the column are equally spaced 3.7 \AA~apart in the
   z-direction (Figure~\ref{fig:perfect_crystal_xyz}). This essentially creates
@@
   to the number of atoms in the unit cell. The intensity will approach infinity as
-  the system size increases.
+  the system size becomes infinitely large.
 
@@
   \centering
-  \begin{tabular}{c c c c c c}
+  \begin{tabular}{c c c c c}
   \toprule
-  $L_z$ (\AA) & Points per column & Number of Pores &  Number of Atoms & R-$\pi$ Intensity & FWHM ($\AA^{-1}$) \\
+  $L_z$ (\AA) & Points per column & Number of Pores &  Number of Atoms & R-$\pi$ Intensity\\ %& FWHM ($\AA^{-1}$) \\
   \midrule
-  14.8        &      4            &       4          & 80               & 80               & 0.34  \\
-  18.5        &      5            &       4          & 100              & 100              & 0.34  \\
-  37          &      10           &       4          & 200              & 200              & 0.34  \\
-  14.8        &      4            &       9          & 180              & 180              & 0.36  \\
-  18.5        &      5            &       9          & 225              & 225              & 0.36  \\
-  37          &      10           &       9          & 450              & 450              & 0.36  \\
-  14.8        &      4            &       16         & 320              & 320              & 0.43  \\
-  18.5        &      5            &       16         & 400              & 400              & 0.43  \\
-  37          &      10           &       16         & 800              & 800              & 0.43  \\
+  14.8        &      4            &       4          & 80               & 80              \\ %& 0.34  \\
+  18.5        &      5            &       4          & 100              & 100             \\ %& 0.34  \\
+  37          &      10           &       4          & 200              & 200             \\ %& 0.34  \\
+  14.8        &      4            &       9          & 180              & 180             \\ %& 0.36  \\
+  18.5        &      5            &       9          & 225              & 225             \\ %& 0.36  \\
+  37          &      10           &       9          & 450              & 450             \\ %& 0.36  \\
+  14.8        &      4            &       16         & 320              & 320             \\ %& 0.43  \\
+  18.5        &      5            &       16         & 400              & 400             \\ %& 0.43  \\
+  37          &      10           &       16         & 800              & 800             \\ %& 0.43  \\
   \bottomrule
@@
   \caption{The intensity of R-$\pi$ in a perfect crystal is equal to the number of
-  scatterers in the unit cell.}\label{table:perfect_size_dependence}
+  scatterers in the unit cell. Here, $L_z$ is the length of the unit cell in the z direction which
+  corresponds to number of points per column $\times$ 3.7.}\label{table:perfect_size_dependence}
   \end{table}
@@
   procedure interpolates between bins, the averaged intensities are lower than
-  expected which slightly changes the shape of the peak. This reflection is
-  radially symmetric about the z-axis, so we fit peak widths to cross-sections at
-  (0, y, 1.7)$^{-1}$ \AA.
+  expected which slightly changes the shape of the peak and gives misleading
+  results. This reflection is radially symmetric about the z-axis, so we fit peak
+  widths to cross-sections at (0, y, 1.7)$^{-1}$ \AA (See Figure~\ref{fig:p2p_rpi}).
 
@@
   with pores spaced 42.5 nm and 212.5 nm apart respectively.  The fundamental
-  frequency appears where expected, based on d. Subharmonics follow the
-  fundamental frequency at equally spaced intervals of width $2\pi / d$.
+  frequency appears at $q_y=0$ with magnitude equal to the number of atoms in the
+  unit cell (Note that each system has a different number of atoms). Subharmonics
+  follow the fundamental frequency at equally spaced intervals of width $2\pi /
+  d$.
 
@@
   \caption{The distance between peaks of the structure factor cross-section at
-  (0, y, 1.7) is equal to the distance between pores in q-space. The first off-center
-  peak of each distribution shows the fundamental frequency. The peaks that follow at 
-  higher |$\mathbf{q}$| values are subharmonics. Both systems shown are in unit cells 
-  with dimensions of 42.5 x 42.5 x 3.7 nm. (a) The pore-to-pore spacing was held at 
-  42.5 nm. The unit cell consists of 100 total pores. The first peak is located at 
-  $q_y = .148 \AA^{-1}$ which corresponds to $2\pi / .148 = 42.5 \AA$ in real space. (b)
-  We placed four pores in a unit cell spaced 21.25 nm apart. The first peak appears where
-  expected at $q_y = 0.0296 \AA^{-1}$ and all other peaks are separated by the same distance.
+  (0, y, 1.7) is equal to the distance between pores in q-space. The center 
+  peak of each distribution shows the fundamental frequency. The peaks
+  that follow at higher $\left|\mathbf{q}\right|$ values are subharmonics. Both systems
+  shown are in unit cells with dimensions of 42.5 x 42.5 x 3.7 nm. (a) We held
+  the pore-to-pore spacing constant at 42.5 \AA. The unit cell consists of 100
+  total pores. The first peak off-center peak is located at $q_y = .148 \AA^{-1}$
+  which corresponds to $2\pi / .148 = 42.5 \AA$ in real space. (b) We placed four
+  pores in a unit cell spaced 212.5 \AA~apart. The first peak appears where
+  expected at $q_y = 0.0296 \AA^{-1}$ ($2\pi / 212.5 \AA$) and all other peaks
+  are separated by that same distance.
   }\label{fig:p2p_rpi}
@@
   appear to give the closest fit to the data (see Figure~\ref{fig:fwhm_fits}). We
-  calculated all of FWHMs in ~\ref{table:perfect_size_dependence} using gaussian
+  calculated all of FWHMs in Table~\ref{table:perfect_size_dependence} using gaussian
   fits.
+
+  \textbf{IMPORTANT}: Note that these 'peak widths' are not the same peak widths that are seen 
+  experimentally. If these showed up experimentally, they would appear as dots 
+  parallel to the $q_r$ axis, crossing through R-$\pi$ and in line with R-pores.
+  There is some evidence of this occuring in some of the simulations (ordered parallel 
+  displaced for example).
 
@@
 
-  The distance between pores does not affect the FWHM of the R-$\pi$ peak in
+  The distance between pores does not affect the FWHM of the R-$\pi$ 'peak' in
   the $q_y$ direction.  We held the size of the unit cell constant at 42.5 x 42.5
@@
   optimized fit parameters. There is no statistical difference between the
-  calculated values of each FWHM. The uncertainty is lower for systems with less
-  pores since there are more subharmonics available for curve fitting. The values
-  of FWHM in Table~\ref{fig:perfect_size_dependence} are calculated using model
-  systems with 4 pores and the same box dimensions used here.
+  calculated values of each FWHM (Table~\ref{table:randomly_displaced_columns}).
+  The uncertainty is lower for systems with less pores since there are more
+  subharmonics available for curve fitting.
+
+%BJC: i'm not sure about these results at the moment. I'd prefer to redo them with finer
+% grids. Not sure they add much value anyways. 
+%  The values of FWHM in
+%  Table~\ref{table:perfect_size_dependence} are calculated using model systems
+%  with 4 pores and the same box dimensions used here.
 
@@
   \caption{We placed one column of scatterers at each of 4 pore centers, spaced apart by
-  212.5 nm. Since the y-component of the distance between all scatteres is the same in 
+  212.5 nm. Since the y-component of the distance between all scatterers is the same in 
   all cases, subharmonics appear just as strongly as the fundamental frequency. Since the 
@@
   \end{figure}
-
-  % peaks may artifically broaden upon angle-averaging.
 
@@
   within the unit cell. We held the spacing between each point within each column
-  remained at exactly 3.7 \AA. We created  trajectories of 1000 independent
+  at 3.7 \AA. We created trajectories of 1000 independent
   configurations in order to calculate the average intensity of R-$\pi$. 1000
@@
   column when we randomly displace columns with respect to each other (See
-  Table~\ref{fig:randomly_displaced_columns}).  It is independent of the
+  Table~\ref{table:randomly_displaced_columns}).  It is independent of the
   number of pores (and hence number of columns) in the system. The error 
@@
   of scatterers about the z-axis. We held constant the angle, with respect to the pore
-  center, between scatterers for any given layer. For examples, since there are 5 
+  center, between scatterers for any given layer. For example, since there are 5 
   columns per pore, each layer is made of 5 monomers. The angle made between the two 
@@
 
-  The max intensity of R-$\pi$ and the FWHM of the $q_y$ structure factor
-  cross-section at R-$\pi$ are exactly the same as those of the perfect crystal.
+  In all cases, the maximum intensity of R-$\pi$ is equal to the number of
+  scatterers in the system and the FWHM of the $q_y$ cross-section of the
+  structure factor at R-$\pi$ is 0.37 $\AA^{-1}$, just as the perfect crystal.
 
-  \subsection{Influence of Pore Radius}
+%  \subsection{Influence of Pore Radius}
 
-  The pore radius is inversely proportional to the FWHM of systems made with
-  randomly rotated layers (See Figure~\ref{fig:pore_radius}). This result is
-  not extremely surprsing, although the limits of the relationship suggest 
-  that a pore radius of 0 should give an infinite FWHM (supported by Figure
-  ~\ref{fig:infinite_FWHM}) and an infinitely large pore radius should have 
-  a zero FWHM. This result is also interesting because it suggests that one
-  can measure relative pore radii using X-ray diffraction. The difficulty,
-  which is associated with the phase problem, is deconvoluting the electron
-  density associated with just pore entities.
+%  The pore radius is inversely proportional to the FWHM of systems made with
+%  randomly rotated layers (See Figure~\ref{fig:pore_radius}). This result is not
+%  extremely surprsing, although the limits of the relationship suggest that a
+%  pore radius of 0 should give an infinite FWHM (supported by Figure
+%  ~\ref{fig:infinite_FWHM}) and an infinitely large pore radius should have a
+%  zero FWHM (of course the pore radius is limited by proximity to other pores).
 
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=0.5\textwidth]{pore_radius_FWHM.png}
-  \caption{The FWHM decays with increasing pore radius.}\label{fig:pore_radius}
-  \end{figure}
+%  This result is also interesting because it suggests that one can measure
+%  relative pore radii using X-ray diffraction. The difficulty, which is
+%  associated with the phase problem, is deconvoluting the electron density
+%  associated with just pore entities.
+
+%  Since the maximum intensity of R-$\pi$ in a randomly rotated layer system
+%  does not change with pore radius (it only depends on the total number of
+%  scatterers), the FWHM is really just a measure of the decay of the subharmonics
+%  surrounding $q_y=0$.
+
+%  \begin{figure}[!htb]
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{pore_radius_FWHM.png}
+%  \caption{The FWHM decays with increasing pore radius.}\label{fig:pore_radius}
+%  \end{figure}
 
@@
   gaussian distribution is equal to a fraction of the average distance between scatterers
-  in columns. In the xy-directions, the standard deviation is equal to a fraction 
-  of the pore radius.
+  in columns (d). In the xy-directions, the standard deviation is equal to a fraction 
+  of the pore radius (r).
 
@@
   When we add noise in the z direction, the intensity of R-$\pi$ decays while the
-  FWHM remains infinite.
+  FWHM remains infinite (Figure~\ref{fig:z_noise_columns}).
 
-  When we add noise in the x and y directions, R-$\pi$ has a finite peak width in its 
-  $q_y$ dimension, and the intensity stays constant. We fit a Gaussian function to the 
-  the $q_y$ cross-section in order to determine its FWHM. The FWHM decay is inversely
-  proportional to the amount of noise added.
+  When we add noise in the x and y directions, R-$\pi$ has a finite peak width
+  in its $q_y$ dimension (Figure~\ref{fig:FWHM_fit_columns}), and the intensity
+  stays constant. We fit a Gaussian function to the the $q_y$ cross-section in
+  order to determine its FWHM. The FWHM decay is inversely proportional to the
+  amount of noise added (Figure~\ref{fig:FWHM_columns}).
 
@@
 
+  This mode of broadening of R-$\pi$ is more consistent with the experimental
+  pattern, where the $q_y$ cross-section of R-$\pi$ is a continuous, broad peak.
+
   \subsubsection{Randomly rotated layers}
@@
 
-  When we add noise in the x and y directions, the intensity of R-$\pi$ does not change.
-  The FWHM slowly decays as shown in Figure~\ref{fig:random_layers_xy_noise}
+  When we add noise in the x and y directions, the intensity of R-$\pi$ does
+  not change. The FWHM slowly decays as shown in
+  Figure~\ref{fig:random_layers_xy_noise}. Importantly, the peak is defined by
+  spikes like those shown in Figure~\ref{fig:p2p_rpi}.
 
@@
   \caption{(a) As we add noise in the z-direction, the intensity of R-$\pi$ decreases
-   rapidly to 1. The FWHM goes to infinity when the intensity of R-$\pi$ equals 1.}\label{fig:layers_noise}
+   rapidly to 1. The FWHM decays slowly and then jumps goes to infinity (not pictured) 
+   when the intensity of R-$\pi$ becomes equal to the background intensity. However one 
+   could argue there is no peak at that point. (b) When we add noise in the x and y 
+   directions, the intensity of R-$\pi$ does not change, but the FWHM decays slowly.}\label{fig:layers_noise}
   \end{figure}
@@
   above systems (See Figure~\ref{fig:deltas}). None of the routes explored so far
-  show how R-$\pi$ might broaden. The delta-function behavior does not change
-  when the system is made taller so as to increase the resolution in z. We built
-  a system 10x taller (37 nm), added random column displacement and some noise in
-  the z-direction. R-$\pi$ is still a sharp delta function
-  (Figure~\ref{fig:tall_rpi}).
+  show how R-$\pi$ might broaden in the $q_z$ direction. The delta-function
+  behavior does not change when the system is made taller so as to increase the
+  resolution in z. We built a system 10x taller (37 nm), added random column
+  displacement and some noise in the z-direction. R-$\pi$ is still a sharp delta
+  function (Figure~\ref{fig:tall_rpi}).
 
@@
   \caption{R-$\pi$ still appears to be a delta function even with higher resolution and
-  noise in the z-positions of the scatterers}
+  noise in the z-positions of the scatterers}\label{fig:tall_rpi}
   \end{figure}
@@
   define a covariance matrix to describe the correlation between all pairs of
-  scatterers.  The variance, v, is defined so that the covariance in position of
+  scatterers. The variance is defined so that the covariance in position of
   a scatterer with itself is the same for all scatterers. The covariance in
@@
   typical covariance matrix for a column containing 20 scatterers is shown in
-  Figure~\ref{fig:covariance}. Next, we drew random sample from a multivariate
-  normal distribution defined using the covariance matrix.
+  Figure~\ref{fig:covariance}. Next, we drew random samples from a multivariate
+  normal distribution defined using the covariance matrix, and applied these
+  shifts to the columns of scatterers.
 
-  \begin{figure}
+  \begin{figure}[!htb]
   \centering
@@
   Adding a finite correlation length between scatterers causes R-$\pi$ to
-  broaden. We simulated a system with dimensions of 8.5 x 8.5 x 37 nm, so that
-  there would be 100 scatterers in the z-direction and a fourier bin size of
-  $1/370=0.0027 \\A^{-1}$.
+  broaden in the $q_z$ direction. We simulated a system with dimensions of 8.5 x
+  8.5 x 37 nm, so that there would be 100 scatterers in the z-direction and a
+  fourier bin size of $1/370=0.0027 \AA^{-1}$. There is a clear broadening of
+  R-$\pi$ when scatterers are correlated
+  (Figure~\ref{fig:correlation_comparison}). The maximum intensity of R-$\pi$
+  decreases as the variance in scatterer position increases
+  (Figure~\ref{fig:correlation_decay}), however the intensity of R-$\pi$ does not
+  change when we vary the correlation length while holding the variance constant.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{correlation.png}
+  \caption{}\label{fig:correlation_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{correlation_decay.png}
+  \caption{}\label{fig:correlation_decay}
+  \end{subfigure}
+  \caption{(a) R-$\pi$ broadens in the $q_z$ direction when scatterers are correlated.
+  (b) The intensity of R-$\pi$ as the variance in scatterer position increases.}\label{fig:correlation}
+  \end{figure}
+
+  \section{Conclusion}
+
+  A number of factors influence the shape and intensity of the R-$\pi$
+  reflection. The maximum intensity of the reflection is most strongly influence
+  by thermal disorder in the z-direction. The peak is broadened in the $q_y$ ($q_r$)
+  direction when there is xy-direction thermal disorder in systems with randomly displaced 
+  columns. The peak is broadened in the $q_z$ direction when there is a finite (non-zero)
+  correlation length between scatterers.
 

### 2018-07-14 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex
Many new figures and additions to text

@@
   \subsection{Crystalline liquid crystals}
+
+  \textbf{NEW} There are two ways to set up the pores for this system. The
+  first is to make all pores exactly the same; just copies that are translated to
+  different pore locations (Figure~\ref{fig:same_rotation}). It is not clear
+  whether a perfect crystal of this material would be arranged in this way. The
+  second way is to randomly rotate each pore
+  (Figure~\ref{fig:different_rotation}). In this work we use the latter.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{same_rotation.png}
+  \caption{}\label{fig:same_rotation}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{different_rotation.png}
+  \caption{}\label{fig:different_rotation}
+  \end{subfigure}
+  \caption{A top-down (xy) view of the pore columns. (a) The right pore is an
+  exact duplicate of the left including rotation about the z-axis. (b) The right
+  pore is a duplicate of the left pore but rotated a random amount about the 
+  z-axis.}\label{fig:initial_rotations}
+  \end{figure}
 
@@
   to each column of points. This simulates a system in which columns are
-  uncorrelated.  We shifted coordinates where necessary so that all atoms stayed
+  uncorrelated.  We wrapped coordinates where necessary so that all atoms stayed
   within the unit cell. We held the spacing between each point within each column
@@
 
-  The intensity of R-$\pi$ is equal to the number of scatterers per
-  column when we randomly displace columns with respect to each other (See
-  Table~\ref{table:randomly_displaced_columns}).  It is independent of the
-  number of pores (and hence number of columns) in the system. The error 
-  in the calculated intensities are comparable to the magnitude of the 
-  intensity because the intensity of each configuration in the trajectory
+  \textbf{NEW} We varied the degree to which we shifted each column with
+  respect to other columns. The most we allowed the columns to shift was one full
+  layer. To choose the position of the column, we chose a random displacement
+  between 0 and d, where d is the maximum allowed displacement. We varied d
+  between 0 and 3.7 \AA.
+
+  When d = 3.7 \AA, the intensity of R-$\pi$ is equal to the number of
+  scatterers per column (See Table~\ref{table:randomly_displaced_columns}).  It
+  is independent of the number of pores (and hence number of columns) in the
+  system. The error in the calculated intensities are comparable to the magnitude
+  of the intensity because the intensity of each configuration in the trajectory
   fluctuates so much.
@@
   \end{table}
+
+  \textbf{NEW} As we allow the columns to displace less (lower values of d),
+  the intensity of R-$\pi$ increases (See Figure~\ref{fig:column_displacement}).
+  Once there is no displacement, the intensity of R-$\pi$ matches that of a
+  perfect crystal. The intensity of R-$\pi$ in our system is likely boosted by
+  correlation between columns.
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{column_displacement.png}
+  \caption{As we increase the amount that columns are allowed to displaced relative
+  to each other, the intensity of R-$\pi$ decreases.}\label{fig:column_displacement}
+  \end{figure}
 
@@
 
+  \textbf{NEW} There is no major difference in the intensity of R-$\pi$ between
+  a perfect crystal and a system with randomly rotated layers. In the z
+  direction, R-$\pi$ remains constant since the z components of the points are
+  spaced exactly 3.7 \AA apart. The maximum intensity of R-$\pi$ is at ($q_x,
+  q_y, q_z$) = (0, 0, 1.7) so there is no contribution from the x or y
+  components. Figure~\ref{fig:perfect_v_random_layers} shows a comparison of the
+  cross-section of R-$\pi$ along $q_y=0$. On the surface it appears that there is
+  a difference between them at high values of $q_y$. However, this is dependent
+  on the initial configuration of the perfect crystal system. The system with
+  randomly rotated layers will always look as it does if a sufficient number of
+  configurations are included in the calculation of the structure factor. The
+  perfect system is in agreement with the randomly rotated layer system at low
+  values of $q_y$, corresponding to scatteres spaced far apart, however it begins
+  to deviate at large $q_y$, where it describes the spatial relationship between
+  scatterers in a single pore. In the perfect system, pores are randomly rotated
+  with respect to each other (See Figure~\ref{fig:same_rotation}), so the spatial
+  relationship changes each time a system is set up. It will not average out since
+  each frame is exactly the same, but if enough pores are added, the 2 
+  cross-sections will match (See Figure~\ref{fig:perfect_v_random_100pores}). 
+  If we create a perfect crystal system where pores are duplicated and translated, but
+  not rotated (See Figure~\ref{fig:same_rotation}), the subharmonics
+  at large $q_y$ are quite pronounced (Figure~\ref{fig:perfect_crystal_same_rotation})
+  due to the increase in ordering in the $q_y$ direction. The peaks are likely
+  geometrically related to the spacing between points within pores, but it is 
+  not important to get to the bottom of that here.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{perfect_v_random_layers.png} 
+  \caption{}\label{fig:perfect_v_random_layers}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{perfect_v_random_100pores.png} 
+  \caption{}\label{fig:perfect_v_random_100pores}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{perfect_crystal_same_rotation_qy.png} 
+  \caption{}\label{fig:perfect_crystal_same_rotation}
+  \end{subfigure}
+  \caption{\textbf{NEW} Shown are cross-sections of the 3D structure factor
+  along $q_y$ at the $q_z$ value of R-$\pi$. We compare the cross-section for 
+  a perfect crystal system and a system where layers are randomly rotated with
+  respect to vertically adjacent layers. (a) When systems are made with 4 pores,
+  the cross-sections agree at low $q_y$ values, however they diverge at higher
+  values of $q_y$. (b) When we build the systems with 100 pores, the cross-sections
+  are in close agreement. (c) If we do not rotate the pores in the perfect crystal
+  system, there are large spikes at high values of $q_y$ due to order within pores.}\label{fig:perfect_v_layers}
+  \end{figure}
+
 %  \subsection{Influence of Pore Radius}
@@
 
+  \subsubsection{\textbf{NEW} Perfect Crystal}
+
+  When we add z-direction gaussian noise to the lattice sites in the perfect
+  crystal, the intensity of R-$\pi$ drops precipitously as noise is increased
+  (Figure~\ref{fig:z_noise_perfect}).  However, the FWHM in the $q_y$ direction
+  is not affected by this noise.
+
+  When we add gaussian noise in the x and y directions, the intensity of
+  R-$\pi$ does not change, however the FWHM sharpens with increasing noise
+  (Figure~\ref{fig:xy_noise_perfect}).
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{z_noise_perfect.png}
+  \caption{}\label{fig:z_noise_perfect}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{xy_noise_perfect.png}
+  \caption{}\label{fig:xy_noise_perfect}
+  \end{subfigure}
+  \caption{(a) The intensity of R-$\pi$ decreases as the amount of z-direction
+  noise increases. (b) The FWHM decreases as noise in the x and y directions
+  increases.}\label{fig:perfect_noise}
+  \end{figure}
+
   \subsubsection{Randomly displaced columns}
 
-  When we add noise in the z direction, the intensity of R-$\pi$ decays while the
-  FWHM remains infinite (Figure~\ref{fig:z_noise_columns}).
+  When we add noise in the z direction, the intensity of R-$\pi$ decays
+  (Figure~\ref{fig:z_noise_columns}).
 
@@
 
-  \subsection{Finite z-correlations}
+  \subsubsection{Finite z-correlations}
 
@@
 
+  \subsubsection{\textbf{NEW} Systems with the "right" amount of noise}
+
+  For a better understanding of the reasons why R-$\pi$ appears as it does in
+  our simulated systems, we added a similar amount of noise to the model system
+  as that seen in our simulations. Table ~\ref{table:simulation_noise} shows the
+  amount of thermal noise in each dimension of the simulated system. We obtained
+  those values by calculating the standard deviation in each dimension of the
+  center of mass head group location from reference locations. We took the
+  reference locations as the average center of mass of each head group. The
+  standard deviations reported are only for frames over which we calculated the
+  simulated diffraction patterns.
+
+  \begin{table}
+  \centering
+  \begin{tabular}{c c c c}
+  \toprule
+  System                         &   $\sigma_x$ ($\AA$) &   $\sigma_y$ ($\AA$) & $\sigma_z$ ($\AA$) \\
+  \midrule
+  Sandwiched, Ordered            &      0.31            &     0.33             &     0.34           \\
+  Parallel Displaced, Ordered    &      0.51            &     0.52             &     0.30           \\
+  Sandwiched, Disordered         &      0.41            &     0.57             &     0.32           \\
+  Parallel Displaced, Disordered &      0.39            &     0.31             &     0.33           \\
+  \bottomrule
+  \end{tabular}
+  \caption{Thermal noise in each dimension of the center of mass of monomer head groups for 
+  simulated LLC systems}\label{table:simulation_noise}
+  \end{table}
+
+  Although the head groups do not move much in the equilibrated portion of the
+  simulation, they are not arranged perfectly into columns. There is quenched
+  disorder present from early in the simulation. To account for this noise, we
+  measured the deviation of the center of masses from idealized positions. To
+  calculate deviations in the x and y dimensions, we calculated the distance
+  between each center of mass and the pore center. The distribution of the radial
+  distance between each center of mass and the pore center, for the ordered
+  sandwiched configuration, is shown in Figure~\ref{fig:xy_com_distribution}. To
+  calculate deviations in the z dimension, we estimated the distance between
+  layers to be the average z-box dimension divided by the number of scatterers
+  per column (20 in the simulated system). Then we measured the deviation between
+  the z position of each center of mass and its corresponding average z-layer
+  position. Histograms of the deviations, for the ordered sandwiched
+  configuration, are in Figure~\ref{fig:z_com_distribution}. We use the standard
+  deviation of each distribution in Figure~\ref{fig:com_distribution} in order to
+  place points in our model systems. The standard deviations for all systems
+  are given in Table~\ref{table:com_sigmas}.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{xy_com_distribution.png}
+  \caption{}\label{fig:xy_com_distribution}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{z_com_distribution.png}
+  \caption{}\label{fig:z_com_distribution}
+  \end{subfigure}
+  \caption{}\label{fig:com_distribution}
+  \end{figure}
+
+  \begin{table}[!htb]
+  \centering
+  \begin{tabular}{c c c}
+  \toprule
+  System                         &   $\sigma_r$ ($\AA$) &   $\sigma_z$ ($\AA$) \\
+  \midrule
+  Sandwiched, Ordered            &      2.30            &     1.48             \\
+  Parallel Displaced, Ordered    &      2.28            &     1.45             \\
+  Sandwiched, Disordered         &      2.93            &     1.58             \\
+  Parallel Displaced, Disordered &      2.63            &     1.65             \\
+  \bottomrule
+  \end{tabular}
+  \caption{Thermal noise in each dimension of the center of mass of monomer
+  head groups for simulated LLC systems}\label{table:com_sigmas}
+  \end{table}
+
+  For a good structural comparison, we set up a model system that mimics the
+  ordered sandwiched configuration. We stacked scatterers 4.4 \AA apart and
+  created pores with a radius of 6.6 \AA in order to be consistent with the
+  values used to calculate the deviations in Table~\ref{table:com_sigmas}. We
+  created an initial configuration with noise in the placement of points based on
+  the values in Table~\ref{table:com_sigmas}. We made the scatterers correlated
+  in the z-direction with a correlation length equal to 20 \AA which is about
+  what we've measured in the simulations. Using the initial configuration, we
+  created 1000 frames to which we added thermal noise in accordance with that
+  measured and recorded in Table~\ref{table:simulation_noise}. The result is a
+  center-of-mass trajectory that is configured and behaves similarly to the
+  simulation trajectory. We can use that model to tune the various influences
+  on R-$\pi$.
+
+  The intensity of R-$\pi$ is strongly dependent on the initial configuration.
+  Each time a model system is generated, the initial configuration is different
+  than the previous model system. The thermal noise added does not compensate
+  for these differences. We ran 40 different model systems with the only 
+  difference being the initial randomization. The average R-$\pi$ intensity of the 
+  40 trials was 25.7 $\pm$ 9.4. This spread has important implications for the
+  reproducibility of our data since there is velocity randomization during the
+  initial equilibration. Also, this initial configuration dependence is not 
+  very useful for analyzing trends.
+
+  We observe the same R-$\pi$ intensity when each frame of the trajectory is
+  randomized. We created a trajectory of 1000 frames. We set up each frame as
+  described in the paragraph before last, however with each frame independent. The
+  average R-$\pi$ intensity over 1000 frames was 25.4, in close agreement with
+  that calculated for the 40 trials of 100 dependent configurations in the
+  previous paragraph. We can use this type of setup to analyze trends.
+
+  Allowing columns to displace further with respect to each other causes the
+  intensity of R-$\pi$ to decrease (Figure~\ref{fig:ld}). In all of the above
+  systems, we placed columns at exactly the same z displacement. Here we allowed
+  them to displace from their initial centers as a function of the fraction of
+  the distance between layers.
+
+  Qualitatively, we can make R-$\pi$ look the most like experiment when columns
+  move independently (See Figure~\ref{fig:rzplots}). As we decrease the
+  dependence between columns, the intensity of R-$\pi$ decreases and the
+  reflection spreads out in the $q_r$ direction. With any amount of dependence
+  between columns, R-$\pi$ sharpens at the center of the reflection.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{rzplot_ld0.png}
+  \caption{}\label{fig:rzplot_ld0}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{rzplot_ld33.png}
+  \caption{}\label{fig:rzplot_ld33}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{rzplot_ld66.png}
+  \caption{}\label{fig:rzplot_ld66}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{rzplot_ld1.png}
+  \caption{}\label{fig:rzplot_ld1}
+  \end{subfigure}
+  \caption{As we allow layers to move more independently, the intensity of
+  R-$\pi$ decreases and spreads out in the $q_r$ direction.}\label{fig:rzplots}
+  \end{figure}
+
+  Again, R-$\pi$ decreases in response to thermal noise (See 
+  Figure~\ref{fig:td}). We varied the amount of thermal noise from a 100 \%
+  decrease to a 100 \% increase in noise in each dimension.
+
+  An increased correlation length causes a modest, linear increase in the
+  intensity of R-$\pi$ (Figure~\ref{fig:cl}). The effect is not nearly as
+  pronounced as z-directional noise and column displacement.
+
+  As we increase the amount of noise in the initial, quenched disordered
+  configuration, the intensity of R-$\pi$ decreases (Figure~\ref{fig:IC}).  We
+  changed the amount of order in the initial configuration by scaling the noise
+  used during placement from -100 \% to 100 \%. We scaled noise in all three
+  dimensions, however we know that the maximum intensity of R-$\pi$ will only be
+  influenced by noise in the z direction.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{ld.png}
+  \caption{}\label{fig:ld}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{td.png}
+  \caption{}\label{fig:td}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{cl.png}
+  \caption{}\label{fig:cl}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{IC.png}
+  \caption{}\label{fig:IC}
+  \end{subfigure}
+  \caption{(a) The intensity of R-$\pi$ decreases as the layers become more
+  independent. (b) The intensity of R-$\pi$ decreases when thermal disorder
+  decreases. (c) The intensity of R-$\pi$ increases with the correlation length.
+  (d) The intensity of R-$\pi$ decreases as more noise is added to the initial
+  configuration.}\label{fig:sim_comp}
+  \end{figure}
+
   \section{Conclusion}

### 2018-07-19 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex
edits for clarification

@@
   Crystallography}. For $\mathbf{q}=\mathbf{0}$, the atomic form factor is equal to the 
-  number of electrons possessed by the atom.
+  number of electrons possessed by the atom. In order to appropriately incorporate
+  the atomic form factor, one can model each atom as a gaussian sphere of electron
+  density whose center has a magnitude equal to the atom's atomic weight.
 
@@
 
-  The distance, d, between peaks in the $q_y$ cross-sections of the structure
-  factor is equal to $2\pi / d$ (Figure~\ref{fig:p2p_rpi}). We looked at systems
-  with pores spaced 42.5 nm and 212.5 nm apart respectively.  The fundamental
-  frequency appears at $q_y=0$ with magnitude equal to the number of atoms in the
-  unit cell (Note that each system has a different number of atoms). Subharmonics
-  follow the fundamental frequency at equally spaced intervals of width $2\pi /
-  d$.
+  The distance between peaks in the $q_y$ cross-sections of the structure
+  factor is equal to $2\pi / d$ (Figure~\ref{fig:p2p_rpi}), where d is the
+  distance between pores. We looked at systems with pores spaced 42.5 nm and
+  212.5 nm apart respectively. The fundamental frequency appears at $q_y=0$ with
+  magnitude equal to the number of atoms in the unit cell (Note that each system
+  has a different number of atoms). Subharmonics follow the fundamental frequency
+  at equally spaced intervals of width $2\pi / d$.
 
@@
 
-  We quantified the peak width by fitting gaussian curves to the R-$\pi$ peak
-  cross-sections and measuring ther full width at half maximum. Gaussian profiles
-  appear to give the closest fit to the data (see Figure~\ref{fig:fwhm_fits}). We
-  calculated all of FWHMs in Table~\ref{table:perfect_size_dependence} using gaussian
-  fits.
+  We fit curves to the peaks of the cross-section of $q_y$ and measurd their
+  full width at half maximum (FWHM). Gaussian profiles appear to give the closest
+  fit to the data (see Figure~\ref{fig:fwhm_fits}). We calculated all of FWHMs in
+  Table~\ref{table:perfect_size_dependence} using gaussian fits.
 
-  \textbf{IMPORTANT}: Note that these 'peak widths' are not the same peak widths that are seen 
-  experimentally. If these showed up experimentally, they would appear as dots 
-  parallel to the $q_r$ axis, crossing through R-$\pi$ and in line with R-pores.
-  There is some evidence of this occuring in some of the simulations (ordered parallel 
-  displaced for example).
+  \textbf{IMPORTANT}: Note that the FWHM does not translate to the peak widths
+  that are seen experimentally. Rather it is a measure of the decay in the
+  intensity of the off center peaks. Experimentally, the center peak is the only
+  peak that appears and it is broadened. If the peaks here showed up
+  experimentally, they would appear as dots parallel to the $q_r$ axis, crossing
+  through R-$\pi$ and in line with R-pores. There is some evidence of this
+  occuring in some of the simulations (ordered parallel displaced for example).
 
@@
   The uncertainty is lower for systems with less pores since there are more
-  subharmonics available for curve fitting.
-
-%BJC: i'm not sure about these results at the moment. I'd prefer to redo them with finer
-% grids. Not sure they add much value anyways. 
-%  The values of FWHM in
-%  Table~\ref{table:perfect_size_dependence} are calculated using model systems
-%  with 4 pores and the same box dimensions used here.
+  peaks available for curve fitting.
 
@@
 
-  The real system is far from a perfect crystal. Here we explore the influence
-  of 4 sources of disorder on the intensity of R-$\pi$:
+  The real system is far from a perfect crystal. In the proceeding section, we
+  explore the influence of 4 sources of disorder on the intensity of R-$\pi$:
   \begin{enumerate}
@@
 
-  When d = 3.7 \AA, the intensity of R-$\pi$ is equal to the number of
-  scatterers per column (See Table~\ref{table:randomly_displaced_columns}).  It
-  is independent of the number of pores (and hence number of columns) in the
-  system. The error in the calculated intensities are comparable to the magnitude
-  of the intensity because the intensity of each configuration in the trajectory
-  fluctuates so much.
+  When d = 3.7 \AA, meaning columns are completely uncorrelated, the intensity
+  of R-$\pi$ is equal to the number of scatterers per column (See
+  Table~\ref{table:randomly_displaced_columns}).  It is independent of the number
+  of pores (and hence number of columns) in the system. The error in the
+  calculated intensities are comparable to the magnitude of the intensity because
+  the intensity of each configuration in the trajectory fluctuates so much.
 
@@
   \end{tabular}
-  \caption{The intensity of R-$\pi$ is equal to the number of scatters in 
-   each column when columns are uncorrelated.}\label{table:randomly_displaced_columns}
+  \caption{The intensity of R-$\pi$ is equal to the number of scatters in each
+	  column when columns are uncorrelated. Note that reproducing these results
+	  requires a very fine histogram, and thus a much more expensive calculation. The
+	  default binning scheme (100 bins in each dimension) gives slightly misleading
+	  answers.
+   }\label{table:randomly_displaced_columns}
   \end{table}
@@
   Once there is no displacement, the intensity of R-$\pi$ matches that of a
-  perfect crystal. The intensity of R-$\pi$ in our system is likely boosted by
-  correlation between columns.
+  perfect crystal. The intensity of R-$\pi$ in the simulated system is likely
+  boosted by the built-in correlation between columns.
 
@@
   \includegraphics[width=0.5\textwidth]{column_displacement.png}
-  \caption{As we increase the amount that columns are allowed to displaced relative
+  \caption{As we increase the amount that columns are allowed to displace relative
   to each other, the intensity of R-$\pi$ decreases.}\label{fig:column_displacement}
@@
   (Figure~\ref{fig:random_columns_qy}) shows non-decaying noise centered near 10,
-  the same R-$\pi$ intensity in Table~\ref{table:randomly_displaced_columns}. The 
-  angle averaged pattern (Figure~\ref{fig:random_columns_rzplot}) further illustrates
-  the diffraction lines which characterize this type of system.
+  the same R-$\pi$ intensity measured and shown in
+  Table~\ref{table:randomly_displaced_columns}. The angle averaged pattern
+  (Figure~\ref{fig:random_columns_rzplot}) further illustrates the diffraction
+  lines which characterize this type of system.
 
@@
   \end{subfigure}
-  \caption{}\label{fig:random_columns_rpi_width}
+  \caption{When columns are uncorrelated, (a) the FWHM of the $q_y$
+	  cross-section of the structure factor is infinite with a magnitude equal to the
+	  number of scatterers per column. (b) The 2D structure factor angle averaged 
+          about the z-axis shows diffraction lines spaced apart by 2$\pi$/d where d is the
+          distance between scatterers in the z-direction.}\label{fig:random_columns_rpi_width}
   \end{figure}
@@
    and thus a much more expensive calculation. The default binning scheme (100 bins in each dimension) gives slightly
-   misleading answers.}\label{table:randomly_displaced_columns}
+   misleading answers.}\label{table:randomly_rotated_layers}
   \end{table}
@@
   scatterers in the system and the FWHM of the $q_y$ cross-section of the
-  structure factor at R-$\pi$ is 0.37 $\AA^{-1}$, just as the perfect crystal.
+  structure factor at R-$\pi$ is 0.37 $\AA^{-1}$
+  (Figure~\ref{table:randomly_rotated_layers}), just as the perfect crystal.
 
@@
   direction, R-$\pi$ remains constant since the z components of the points are
-  spaced exactly 3.7 \AA apart. The maximum intensity of R-$\pi$ is at ($q_x,
+  spaced exactly 3.7 \AA~apart. The maximum intensity of R-$\pi$ is at ($q_x,
   q_y, q_z$) = (0, 0, 1.7) so there is no contribution from the x or y
@@
   perfect system is in agreement with the randomly rotated layer system at low
-  values of $q_y$, corresponding to scatteres spaced far apart, however it begins
+  values of $q_y$, corresponding to scatterers spaced far apart, however it begins
   to deviate at large $q_y$, where it describes the spatial relationship between
@@
 
-  We added gaussian noise in each dimension to observe its influence on the intensity
-  of R-$\pi$ and the FWHM. For the z-direction, the standard deviation of the 
-  gaussian distribution is equal to a fraction of the average distance between scatterers
-  in columns (d). In the xy-directions, the standard deviation is equal to a fraction 
-  of the pore radius (r).
+  We added gaussian noise in each dimension to observe its influence on the
+  intensity of R-$\pi$ and the FWHM. For the z-direction, the standard deviation
+  of the gaussian distribution is equal to a fraction of the average distance
+  between scatterers in columns (d). In the xy-directions, the standard deviation
+  is equal to a fraction of the pore radius (r).
 
@@
   (Figure~\ref{fig:z_noise_perfect}).  However, the FWHM in the $q_y$ direction
-  is not affected by this noise.
+  is unaffected by this noise (not pictured).
 
@@
   R-$\pi$ does not change, however the FWHM sharpens with increasing noise
-  (Figure~\ref{fig:xy_noise_perfect}).
+  (Figure~\ref{fig:xy_noise_perfect}). In other words, the intensity of
+  subharmonics decrease, resulting in a smaller FWHM.
 
@@
   in its $q_y$ dimension (Figure~\ref{fig:FWHM_fit_columns}), and the intensity
-  stays constant. We fit a Gaussian function to the the $q_y$ cross-section in
-  order to determine its FWHM. The FWHM decay is inversely proportional to the
-  amount of noise added (Figure~\ref{fig:FWHM_columns}).
+  stays constant. This is different than what was previously shown
+  (Figure~\ref{fig:fwhm_fits} for example). These are continuous peaks that
+  represent broadening of the fundamental R-$\pi$ peak. We fit a Gaussian
+  function to the the $q_y$ cross-section in order to determine its FWHM. The
+  FWHM decay is inversely proportional to the amount of noise added
+  (Figure~\ref{fig:FWHM_columns}).
 
@@
    broaden in the y-direction with a continuous intensity distribution that can be
-   fit to a gaussian. (c) This FWHM decreases as the inverse of the amount of 
+   fit to a gaussian. (c) The FWHM decreases as the inverse of the amount of 
    noise added.}\label{fig:columns_noise}
@@
   \caption{(a) As we add noise in the z-direction, the intensity of R-$\pi$ decreases
-   rapidly to 1. The FWHM decays slowly and then jumps goes to infinity (not pictured) 
+   rapidly to 1. The FWHM increases slowly and then jumps to infinity (not pictured) 
    when the intensity of R-$\pi$ becomes equal to the background intensity. However one 
@@
   \includegraphics[width=0.5\textwidth]{covariance.png}
-  \caption{}\label{fig:covariance}
+  \caption{An example covariance matrix used to place scatterers with a
+	  correlation length. The scatterer centers are equally spaced in the
+	  z-direction. Each value in the diagram represents the covariance between pairs
+	  of scatterers. Diagonal entries represent covariance in position of scatterers
+	  with themselves. The covariance decays exponentially as scatterers space apart
+	  further.}\label{fig:covariance}
   \end{figure}
@@
   \end{subfigure}
-  \caption{(a) R-$\pi$ broadens in the $q_z$ direction when scatterers are correlated.
-  (b) The intensity of R-$\pi$ as the variance in scatterer position increases.}\label{fig:correlation}
+  \caption{(a) R-$\pi$ broadens in the $q_z$ direction when scatterers are
+	  correlated. (b) The intensity of R-$\pi$ decreases as the variance in
+	  scatterer position increases.}\label{fig:correlation}
   \end{figure}
@@
   \end{tabular}
-  \caption{Thermal noise in each dimension of the center of mass of monomer
-  head groups for simulated LLC systems}\label{table:com_sigmas}
+  \caption{Uncertainty in the deviation of monomer head groups from ideal 
+          positions in each dimension for simulated LLC systems}\label{table:com_sigmas}
   \end{table}
@@
   Each time a model system is generated, the initial configuration is different
-  than the previous model system. The thermal noise added does not compensate
-  for these differences. We ran 40 different model systems with the only 
-  difference being the initial randomization. The average R-$\pi$ intensity of the 
-  40 trials was 25.7 $\pm$ 9.4. This spread has important implications for the
-  reproducibility of our data since there is velocity randomization during the
-  initial equilibration. Also, this initial configuration dependence is not 
+  than the previous model system. The thermal noise added does not compensate for
+  these differences. We ran 40 different model systems with the only difference
+  being the initial configuration randomization. The average R-$\pi$ intensity of
+  the 40 trials was 25.7 $\pm$ 9.4. This spread has important implications for
+  the reproducibility of our data since there is velocity randomization during
+  the initial equilibration that will randomize the configurations which are 
+  then locked in. Also, this initial configuration dependence is not
   very useful for analyzing trends.
@@
   between columns, R-$\pi$ sharpens at the center of the reflection.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth} 
-  \includegraphics[width=\textwidth]{rzplot_ld0.png}
-  \caption{}\label{fig:rzplot_ld0}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth} 
-  \includegraphics[width=\textwidth]{rzplot_ld33.png}
-  \caption{}\label{fig:rzplot_ld33}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth} 
-  \includegraphics[width=\textwidth]{rzplot_ld66.png}
-  \caption{}\label{fig:rzplot_ld66}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth} 
-  \includegraphics[width=\textwidth]{rzplot_ld1.png}
-  \caption{}\label{fig:rzplot_ld1}
-  \end{subfigure}
-  \caption{As we allow layers to move more independently, the intensity of
-  R-$\pi$ decreases and spreads out in the $q_r$ direction.}\label{fig:rzplots}
-  \end{figure}
 
@@
 
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{rzplot_ld0.png}
+  \caption{}\label{fig:rzplot_ld0}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{rzplot_ld33.png}
+  \caption{}\label{fig:rzplot_ld33}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{rzplot_ld66.png}
+  \caption{}\label{fig:rzplot_ld66}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} 
+  \includegraphics[width=\textwidth]{rzplot_ld1.png}
+  \caption{}\label{fig:rzplot_ld1}
+  \end{subfigure}
+  \caption{As we allow layers to move more independently, the intensity of
+  R-$\pi$ decreases and spreads out in the $q_r$ direction.}\label{fig:rzplots}
+  \end{figure}
+
   \section{Conclusion}
 
-  A number of factors influence the shape and intensity of the R-$\pi$
-  reflection. The maximum intensity of the reflection is most strongly influence
-  by thermal disorder in the z-direction. The peak is broadened in the $q_y$ ($q_r$)
-  direction when there is xy-direction thermal disorder in systems with randomly displaced 
-  columns. The peak is broadened in the $q_z$ direction when there is a finite (non-zero)
+  A number of factors influence the shape and intensity of the R-$\pi$ reflection
+  in our simulated systems.
+
+  The maximum intensity of the reflection is most strongly influenced by
+  disorder in the z-direction. The first source of z-directional disorder is
+  caused by randomization of the initial configuration.  This configuration gets
+  essentially locked into place. The second source is thermal noise during the
+  simulation. The amount of thermal noise is smaller in magnitude than the
+  randomization induced during early equilibration.
+
+  The peak is broadened in the $q_y$ ($q_r$) direction when there is
+  xy-direction thermal disorder in systems with randomly displaced columns. The
+  peak looks most like experiment when columns are completely independent.
+
+  The peak is broadened in the $q_z$ direction when there is a finite (non-zero)
   correlation length between scatterers.

### 2018-08-03 Ben_Manuscripts/structure_paper/Draft.tex
edits for clarification
New figures and R-pi investigation

@@
   %MRS8: did you do a few different things here as sensitivity analysis to show that the finding was robust?  If so, putting some of that in would be useful.
+  %BJC7: make it clear that it is the 280K. Reference all configurations where tilt angles were calculated.
 
@@
 
-  There is not a single reason we can clearly identify for the high intensity of R-$\pi$ in our simulations.
-  We used one-dimensional pair distribution functions of the centers of masses of monomer
-  phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
-  columns and the degree to which they are correlated. These metrics helped us dissect the 
-  various contributions to R-$\pi$. Figure~\ref{fig:correlation} shows $g(z)$ for all 
-  systems tested.
-
-%  The first peak of $g(z)$ is larger in the ordered
-%  basin systems compared to those in the disordered basin. This observation is indicative
-%  of a higher degree of local ordering in the ordered basin systems which causes an
-%  increase in the intensity of R-$\pi$.
-
-  %MRS7: not a strong thesis sentence.
-%  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
-%  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). We used this 
-%  information to understand how far apart monomers stack within monomer columns and
-%  the degree to which they are correlated.
+  % BJC8: Is it necessary to focus in on the parallel displaced system for this section? At this
+  % point in the story, I haven't shown that it gives rise to R-double. I think the simple systems
+  % are conceptually easier to grasp with sandwiched columns. Sliding parallel displaced columns
+  % is harder to imagine, and probably not really how the columns are stacked. The parallel displacement
+  % is probably less exagerated. 
+  % BJC8: that said, if we go with just focusing on parallel displaced, then I can move the R-double section
+  % up before this one.
+  R-$\pi$ is more intense relative to the experimental system. In this section, we use the parallel displaced
+  configuration in the ordered basin as an example, however all systems display this behavior.
+  %since it is the most experimentally consistent system we've studied so far. 
+  The intensity of R-$\pi$ in the ordered parallel displaced system is approximately 3 times
+  larger than experiment (Table~\ref{table:relative_inensities_300K}).
+
+  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections of R-$\pi$ 
+  are in moderate agreement with experiment (Figure~\ref{fig:rpi_exp_comparison}). Each FWHM
+  is larger than experiment. Note that the experimental data is best fit with a Lorentzian 
+  function while the simulated patterns are best fit using a Gaussian function. The experimental
+  pattern also has additional sources of broadening which, if deconvoluted, would increase the discrepancy with
+  simulation.
+  % BJC8: Can add more detail about different types of broadening - instrument / finite resolution broadening (for
+  % experimental case), doppler (gaussian shaped) and pressure broadening (Lorentzian shaped)
+  % See: https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-7
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
+  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
+  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
+  \caption{FWHM = 0.194 $\pm$ 0.013 $\AA^{-1}$}\label{fig:sim_zsection_fit}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
+  \caption{FWHM = 0.962 $\pm$ 0.010 $\AA^{-1}$}\label{fig:sim_rsection_fit}
+  \end{subfigure}
+  \caption{(a) Experimentally, R-$\pi$ broadens in the $q_z$ direction with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when
+  fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
+  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. (c) In our simulations, the FWHM of R-$\pi$ in
+  the $q_z$ direction is 0.194 $\pm$ 0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width
+  of experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01 $\AA^{-1}$ when fit with
+  a Gaussian function, about 20 \% larger than experiment. Note that the large spike in the center is not included
+  in the fit.}\label{fig:rpi_exp_comparison}
+  \end{figure}
+
+  Here we present our understanding of what factors influence the intensity of R-$\pi$ 
+  as well its FWHM in the $q_z$ and $q_r$ directions. We have identified a number of 
+  potential contributions which can be modified in our model by adjusting the simulation
+  conditions, forcefield or initial configuration. We assessed each using a simplified 
+  model. Our simplified model represents each monomer head group as a single point and
+  places them in either a parallel displaced or sandwiched configuration. We apply 
+  various transformations in order to study its simulated diffraction pattern.
+
+  As a baseline, we created a simplified model using the same amount of disorder present
+  in our atomistic simulations. There are two sources of disorder to consider: thermal motion of
+  atoms and quenched disorder which is created by rapid structural rearrangement during
+  early equilibration and is locked into place for the remainder of the simulation time. The
+  latter has important implications for the reproducibility of this work since velocity
+  randomization at the beginning of equilibration will result in different quenched 
+  configurations. We measured thermal disorder by measuring the standard deviation in
+  the distribution of head group center of mass positions from their average positions.
+  We measured quenched disorder by calculating the standard deviation of the distribution 
+  of head group center of masses from their ideal positions. In the z-direction, we measured
+  the deviation of the head group center of masses from an equally spaced column of head groups.
+  In the xy plane, we calculated the deviation in radial position from the pore center and 
+  the angular deviation from equally spaced points surrounding the pore center. The values
+  measured for each system are given in Table~\ref{table:quenched_disorder}. We built a simple
+  system consisting of 1000 independent configurations using these parameters. We also made
+  the simple system 4 times taller in order to get better resolution in the $q_z$ direction. 
+  Figure~\ref{fig:sf_qy_nocorrelation} shows the $q_y$ cross-section of R-$\pi$ generated by
+  simulating the structure factor of the trajectory.
+
+  %BJC8: Need to add thermal noise to this table
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{c|ccc}
+  \toprule
+  System                        & $\sigma_z$ ($\AA$) & $\sigma_\theta$ (rad) & $\sigma_r$ ($\AA$) \\
+  \midrule
+  Ordered Sandwiched            &        1.48        &     0.43              &     2.30           \\
+  Ordered Parallel Displaced    &        1.45        &     0.43              &     2.28           \\ 
+  Disordered Sandwiched         &        1.58        &     0.43              &     2.93           \\
+  Disordered Parallel Displaced &        1.65        &     0.43              &     2.63           \\
+  \bottomrule
+  \end{tabular}
+  \caption{We measured the deviation of the positions of the center of mass of head groups from
+  idealized positions so that we could incorporate the same disorder into our model system.}
+  \label{table:quenched_disorder} 
+  \end{table}
+
+  %BJC8: Create parallel displaced configuration: create sandwiched system. Apply uniform rotation to every other layer
+  %BJC8: I'd like to make the point somewhere that the real configuration is somewhere between sandwiched and the
+  % parallel displaced configuration shown here.
+%  There is no major difference between R-$\pi$ of a parallel displaced system and a 
+%  sandwiched system.
+%  \begin{itemize}
+%  	\item Intensity does not change
+%  	\item 
+%  \begin{itemize}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
+  \caption{}\label{fig:sf_qy_nocorrelation}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
+  \caption{}\label{fig:sf_qy_correlation.png}
+  \end{subfigure} 
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
+  \caption{}\label{fig:sf_qz_correlation.png}
+  \end{subfigure}   
+  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
+  points meant to represent monomer head groups. We added a similar amount of noise to 
+  that seen in our simulations. (a) We added Gaussian noise to each particle in the z, 
+  $\theta$ and r directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
+  peaks. (b) When we make points in each column correlated, the intensity of R-$\pi$ 
+  increases but the sharp peaks remain with the same ratio of intensity between the
+  center and outer peaks. (c) Correlation between scatterers in the z-direction causes
+  R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
+  \end{figure}
+
+  Scatterers in each column are correlated with each other. In the simplified 
+  system described above, we added uncorrelated Gaussian noise in the 
+  z-direction which ignores any interaction head groups might have with each
+  other. To remedy this, we randomly sampled a multivariate normal distribution
+  with the same variance, v, implied by Table~\ref{table:quenched_disorder}. We 
+  defined the distribution using a covariance matrix such that the covariance
+  in position, z, between scatterers decays exponentially from v according to the
+  equation $ve^{-z/L}$, where L is the correlation length. Experimentally, the
+  correlation length can be estimated as the inverse of the FWHM of the $q_z$
+  cross-section of R-$\pi$.  %BJC8: needs references 
+  Accordingly, the correlation length of the experimental system is $\geq$ 9 
+  $\AA$. The value may be larger since the peak is likely broadened for a variety
+  of other reasons. %BJC8: the reasons I can provide more detail on above.  
+  %BJC8: Can show correlation effect on intensity in supporting info
+
+  The correlation length of vertically stacked scatterers in our simulations are
+  in reasonable agreement with experiment. Since it is not feasible for us to simulate
+  membranes with much taller columns for increased $q_z$ resolution, and because the 
+  peak shape is convoluted by the extremely intense maximum of R-$\pi$, we measured 
+  correlation length by plotting the one-dimensional pair distribution function, $g(z)$,
+  for the centers of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). 
+  %We used this 
+  %information to understand how far apart monomers stack within monomer columns and
+  %the degree to which they are correlated.
 
@@
 
+  %BJC8: The next couple paragraphs is all old stuff that can likely be cut down a bit. But I think 
+  % this is where I'd put this discussion.
   Monomers in the ordered basin stack closer together than those in the disordered basin
@@
 
+  Increased thermal noise in the z-direction causes a drop in the intensity of R-$\pi$, however 
+  the $q_r$ profile remains unchanged. 
+  \begin{itemize}
+  	\item Show how I can decrease the intensity by a factor of 3-15 x by just increasing z-direction
+  	thermal noise
+  	\item Can put thermal noise vs. intensity in supporting info.
+  	\item The peaks are still sharp though
+  	\item 3 panel figure : regular intensity, 3x decrease, 15x decrease. Peak shapes all the same
+  \end{itemize}
+
+  When we allow monomer columns to move independently in the z-direction, the intensity
+  of R-$\pi$ drops and the $q_r$ cross-section of the simulated diffraction patterns 
+  smooths out.
+  \begin{itemize}
+  	\item Allowing columns to move independently smooths out the $q_r$ cross-section. Any amount
+  	of dependence results in sharp peaks.
+  	\item R-$\pi$ intensity decreases by up to 10x
+  	\item Can put R-$\pi$ intensity vs. column independence in supporting info.
+  	\item Predict level of independence in simulation (what amount of displacement cause the 
+  	R-$\pi$ profile to look like that shown in Figure 8d).
+  	\item Figure: (a) x \% column displacement give Figure 8d (b) Independent columns give a smooth
+  	curve
+  \end{itemize}
+
+  Increasing thermal noise in the x and y directions causes R-$\pi$ to sharpen in the 
+  $q_r$ direction.
+  \begin{itemize}
+    \item $q_r$ cross-section still too broad
+    \item Adding more thermal noise sharpens it
+    \item Figure: Overlay thinner FWHM plot on top of wider FWHM 
+  \end{itemize}
+
+  We have nearly the right amount of disorder / noise in our system, but correlation 
+  between columns really messes up R-$\pi$.
+
+%  \item Stacked disks (layers)
+%	  \item No influence on intensity
+%	  \item Some influnce on FWHM (?)
+
+%  There is not a single reason we can clearly identify for the high intensity of R-$\pi$ in our simulations.
+%  We used one-dimensional pair distribution functions of the centers of masses of monomer
+%  phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
+%  columns and the degree to which they are correlated. These metrics helped us dissect the 
+%  various contributions to R-$\pi$. Figure~\ref{fig:correlation} shows $g(z)$ for all 
+%  systems tested.
+
+%  The first peak of $g(z)$ is larger in the ordered
+%  basin systems compared to those in the disordered basin. This observation is indicative
+%  of a higher degree of local ordering in the ordered basin systems which causes an
+%  increase in the intensity of R-$\pi$.
+
+  %MRS7: not a strong thesis sentence.
+
   %The amount of noise in the correlation function and the lack of an initial peak suggests that 
@@
 
-  The persistent oscillatory behavior of the correlation function may in part explain the high
-  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
-  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
-  simulated systems, especially the sandwiched configurations, shows peaks which persist across
-  the entire correlation function. If the peaks, at large values of z, instead decay to 1 uniformly,
-  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
-  The monomer head groups in our simulations do not move enough on the timescales simulated to 
-  create the noise which would cause such behavior. See Section S-\ref{S-section:rpi_ft} of the
-  supporting information for illustrative examples.
+%  The persistent oscillatory behavior of the correlation function may in part explain the high
+%  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
+%  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
+%  simulated systems, especially the sandwiched configurations, shows peaks which persist across
+%  the entire correlation function. If the peaks, at large values of z, instead decay to 1 uniformly,
+%  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
+%  The monomer head groups in our simulations do not move enough on the timescales simulated to 
+%  create the noise which would cause such behavior. See Section S-\ref{S-section:rpi_ft} of the
+%  supporting information for illustrative examples.
 

### 2018-08-04 Ben_Manuscripts/structure_paper/Draft.tex
Comments on section 3.2.2

@@
   % up before this one.
+  % MRS9: I think we should start with larger differences rather than smaller, and arguably the greater intensity of R-pi is 
+  % a bigger difference.
+So it's OK ti put R-double after -- (and it could be that sliding sandwiched columns could still give water h-bonding, since they have carboxyl groups that are on average closer together than sandwiched layered ones).
   R-$\pi$ is more intense relative to the experimental system. In this section, we use the parallel displaced
-  configuration in the ordered basin as an example, however all systems display this behavior.
+  configuration in the ordered basin as an example, however 
+%MRS9: should be a little more clear why you mean by ``all systems''.
+In some sense the problem is more that the best explanation might be unaligned columns, which is easier with sandwiched, which are 15 times as much.
+So here it would make more sense to focus on both types of columns, so you can explain how unaligned (sliding) columns also have a mechanism for reduction.
+Note that I don't think the columns have to be dynamically sliding (Which would be hard with all the tails entangled) but can be just off-register statically.
+all systems display this behavior.
   %since it is the most experimentally consistent system we've studied so far. 
@@
   are in moderate agreement with experiment (Figure~\ref{fig:rpi_exp_comparison}). Each FWHM
-  is larger than experiment. Note that the experimental data is best fit with a Lorentzian 
+  is larger than experiment. 
+  %MRS9: state how much larger they are than experiment in the sentence before - big difference beween 30% bigger and 300% bigger.
+Note that the experimental data is best fit with a Lorentzian 
   function while the simulated patterns are best fit using a Gaussian function. The experimental
@@
   simulation.
+  %MRS9: State explicitly in what way the discrepancy would increase, i.e.
+experimental FWHM are broadened by other source (doppler pressure, insttrument broadening) that do no affect the simulated spectra, the experimental spectra may be even narrower than spectra generated from simulations are.
+  %MRS9: one question, do any of the approximations used in the simulation actually lead to broadening that would not be in experiment (gaussian scatterers, etc.
+Also, (semi-related) do Gaussian scatters lead to Gaussian peaks?
+Fourier transforms of Gaussians are Gaussians)
   % BJC8: Can add more detail about different types of broadening - instrument / finite resolution broadening (for
@@
   % See: https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-7
-
+  %MRS 9: it is a little problematic to use two different types of fit, as the FWHM is a little different for each of then.
+Would lead to slight discrepancies from that.
+FWHM is a natural scale parameter for Lorenzians, but not really for Gaussian.
   \begin{figure}
@@
   \end{subfigure}
-  \caption{(a) Experimentally, R-$\pi$ broadens in the $q_z$ direction with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when
+  \caption{
+   %MRS9: suggest something like this to make crystal clear A and B are from the experiments.
+  In experiments ((a) and (b)), 
+%Experimentally,  (a) 
+  (a), R-$\pi$ broadens in the $q_z$ direction with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when
   fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
@@
 
-  Here we present our understanding of what factors influence the intensity of R-$\pi$ 
-  as well its FWHM in the $q_z$ and $q_r$ directions. We have identified a number of 
-  potential contributions which can be modified in our model by adjusting the simulation
-  conditions, forcefield or initial configuration. We assessed each using a simplified 
+%MRS9: Could be stronger thesis.  Suggest
+We have identified a number of potential ways that simulations conditions, forcefield and initial configurations could affect the intensity of R-$\pi$ as well its FWHM in the $q_z$ and $q_r$ directions
+%Here we present our understanding of what factors influence the intensity of R-$\pi$ 
+%  as well its FWHM in the $q_z$ and $q_r$ directions. We have identified a number of 
+%  potential contributions which can be modified in our model by adjusting the simulation
+%  conditions, forcefield or initial configuration. 
+We assessed each using a simplified 
   model. Our simplified model represents each monomer head group as a single point and
@@
   various transformations in order to study its simulated diffraction pattern. 
-
+  %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.
   As a baseline, we created a simplified model using the same amount of disorder present
@@
   randomization at the beginning of equilibration will result in different quenched 
-  configurations. We measured thermal disorder by measuring the standard deviation in
+  configurations. 
+  %MRS9: could be that initial starting configurations would ALSO give rise to different quenched configurations.
+We measured thermal disorder by measuring the standard deviation in
   the distribution of head group center of mass positions from their average positions.
   We measured quenched disorder by calculating the standard deviation of the distribution 
-  of head group center of masses from their ideal positions. In the z-direction, we measured
+  of head group center of masses from their 
+%ideal positions. 
+idealized average positions.
+In the $z$-direction, we measured
   the deviation of the head group center of masses from an equally spaced column of head groups.
-  In the xy plane, we calculated the deviation in radial position from the pore center and 
+  In the $xy$ plane, we calculated the deviation in radial position from the pore center and 
   the angular deviation from equally spaced points surrounding the pore center. The values
@@
   \end{tabular}
-  \caption{We measured the deviation of the positions of the center of mass of head groups from
-  idealized positions so that we could incorporate the same disorder into our model system.}
+  %MRS9: tweaked
+  \caption{Deviation of the positions of the center of mass of head groups from
+  idealized positions to use as simulated disorder into our model system.}
   \label{table:quenched_disorder} 
@@
   % parallel displaced configuration shown here.
+  %MRS9: better to say ``data is most consistent with the idea that the real configuration is somewhere between''
 %  There is no major difference between R-$\pi$ of a parallel displaced system and a 
@@
 
+%MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
   \begin{figure}[!htb]
@@
   points meant to represent monomer head groups. We added a similar amount of noise to 
-  that seen in our simulations. (a) We added Gaussian noise to each particle in the z, 
-  $\theta$ and r directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
+  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
+  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
   peaks. (b) When we make points in each column correlated, the intensity of R-$\pi$ 
   increases but the sharp peaks remain with the same ratio of intensity between the
-  center and outer peaks. (c) Correlation between scatterers in the z-direction causes
+  center and outer peaks. (c) 
+  %MRS9: I'm not sure what you mean by ``correlation'' broadening peaks here.  Do you mean replacing exact periodicity by 
+  %correlated random points  Because that reduces correlation (from 100% to less than 100%).
+Correlation between scatterers in the $z$-direction causes
   R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
+  %MRS9: in c, weird that the orange peaks are broader, but taller. Not sure I understand. 
   \end{figure}
@@
   other. To remedy this, we randomly sampled a multivariate normal distribution
-  with the same variance, v, implied by Table~\ref{table:quenched_disorder}. We 
+  with the same 
+  %variance, v, 
+  standard deviation, $\sigma$.
+  implied by Table~\ref{table:quenched_disorder}. We 
   defined the distribution using a covariance matrix such that the covariance
@@
   The distance between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all 
-  cases. This behavior is not surprising since GAFF models atoms as point charges and does not 
+  cases,
+  %MRS9: added
+  with disordered basins at the high part of that range 0.2 and 0.3 \AA~more distant.
+  %MRS9: GAFF could OVER predict pi-pi stacking, best to include citations here that it does indeed overpredict.
+This behavior is not surprising since GAFF models atoms as point charges and does not 
   appropriately model the aromatic $\pi-\pi$ interactions which would make it more energetically
-  favorable for the monomers to stack closer together. Additionally, it is possible that the 
+  favorable for the monomers to stack closer together. 
+Additionally, it is possible that the 
   tails prevent close stacking of monomer head groups and we do not achieve the timescales 
@@
   basin systems are likely the best choice for transport studies. 
+%MRS9: make it clearer if the last sentence is a conclusion based on the other evidence in the paragraph.
 
@@
   	\item Predict level of independence in simulation (what amount of displacement cause the 
-  	R-$\pi$ profile to look like that shown in Figure 8d).
+  	R-$\pi$ profile to look like that shown in Figure 8d). %MRS9: this is a bit complicated, since it could be a combination of factors.
   	\item Figure: (a) x \% column displacement give Figure 8d (b) Independent columns give a smooth
-  	curve
+  	curve %MRS9: not quite sure what you are talking about in this figure.  Could you give more information?
   \end{itemize}
@@
   Increasing thermal noise in the x and y directions causes R-$\pi$ to sharpen in the 
-  $q_r$ direction.
+  $q_r$ direction. %MRS9: this is unanticiated (noise creating sharpening) so will have to make it clear.
   \begin{itemize}
@@
 
+%MRS9: the statement below is pretty strong, need to back it up.  We know that we have quenched noise, which is a type of over-ordering - is that taken into account?  
   We have nearly the right amount of disorder / noise in our system, but correlation 
@@
 
-  The system size does not significantly alter the intensity of R-$\pi$. We equilibrated a 
+  The system size 
+  %MRS9: added
+  in the $z$-direction.
+  does not significantly alter the intensity of R-$\pi$. We equilibrated a 
   sandwiched system with twice as many monomers per column so that the system size doubled in 

### 2018-08-06 Ben_Manuscripts/structure_paper/Draft.tex
New figures for R-pi explanation

@@
 So it's OK ti put R-double after -- (and it could be that sliding sandwiched columns could still give water h-bonding, since they have carboxyl groups that are on average closer together than sandwiched layered ones).
-  R-$\pi$ is more intense relative to the experimental system. In this section, we use the parallel displaced
-  configuration in the ordered basin as an example, however 
+  %BJC9: keeping above comments for reference
+
+  R-$\pi$ is more intense relative to the experimental system. The difference in intensity
+  ranges from 3 times too high in the ordered parallel displaced system to 15 times too 
+  high in the ordered sandwiched configuration (Table~\ref{table:relative_inensities_300K}).
+%BJC9: keeping below comment for reference  
 %MRS9: should be a little more clear why you mean by ``all systems''.
@@
 Note that I don't think the columns have to be dynamically sliding (Which would be hard with all the tails entangled) but can be just off-register statically.
-all systems display this behavior.
-  %since it is the most experimentally consistent system we've studied so far. 
-  The intensity of R-$\pi$ in the ordered parallel displaced system is approximately 3 times
-  larger than experiment (Table~\ref{table:relative_inensities_300K}).
 
   The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections of R-$\pi$ 
-  are in moderate agreement with experiment (Figure~\ref{fig:rpi_exp_comparison}). Each FWHM
-  is larger than experiment. 
-  %MRS9: state how much larger they are than experiment in the sentence before - big difference beween 30% bigger and 300% bigger.
-Note that the experimental data is best fit with a Lorentzian 
-  function while the simulated patterns are best fit using a Gaussian function. The experimental
-  pattern also has additional sources of broadening which, if deconvoluted, would increase the discrepancy with
-  simulation.
+  are in moderate agreement with experiment (Figure~\ref{fig:rpi_exp_comparison}). The
+  FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the $q_r$ cross-section
+  FWHM is 21\% larger than experiment. Note that the experimental data is best fit with a Lorentzian 
+  function while the simulated patterns are best fit using a Gaussian function. The simulated
+  spectra do not incorporate the effects of pressure broadening and instrumental broadening
+  which would alter the peak shape. In the absence of these and other peak broadening effects,
+  the experimental peak would actually be narrower, further increasing the discrepancy with simulation.
+
   %MRS9: State explicitly in what way the discrepancy would increase, i.e.
@@
   \caption{
-   %MRS9: suggest something like this to make crystal clear A and B are from the experiments.
-  In experiments ((a) and (b)), 
-%Experimentally,  (a) 
-  (a), R-$\pi$ broadens in the $q_z$ direction with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when
-  fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
-  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. (c) In our simulations, the FWHM of R-$\pi$ in
+  In experiments ((a) and (b)), (a), R-$\pi$ broadens in the $q_z$ direction with a FWHM of 
+  0.110 $\pm$ 0.003 $\AA^{-1}$ when fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
+  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. In our simulations ((c) and (d)), (c) the FWHM of R-$\pi$ in
   the $q_z$ direction is 0.194 $\pm$ 0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width
@@
   %MRS9: Could be stronger thesis.  Suggest
-We have identified a number of potential ways that simulations conditions, forcefield and initial configurations could affect the intensity of R-$\pi$ as well its FWHM in the $q_z$ and $q_r$ directions
-%Here we present our understanding of what factors influence the intensity of R-$\pi$ 
-%  as well its FWHM in the $q_z$ and $q_r$ directions. We have identified a number of 
-%  potential contributions which can be modified in our model by adjusting the simulation
-%  conditions, forcefield or initial configuration. 
-We assessed each using a simplified 
-  model. Our simplified model represents each monomer head group as a single point and
-  places them in either a parallel displaced or sandwiched configuration. We apply 
-  various transformations in order to study its simulated diffraction pattern. 
+  We have identified a number of potential ways that simulation conditions, forcefield 
+  and initial configurations could affect the intensity of R-$\pi$ as well its FWHM in 
+  the $q_z$ and $q_r$ directions. We assessed each using a simplified model. Our 
+  simplified model represents each monomer head group as a single point and places them
+  in either a parallel displaced or sandwiched configuration. We chose to explore
+  the influence of thermal noise in each dimension, correlation between scatterers within
+  columns, as well as correlation between columns since these are the variables we 
+  believe have the largest influence on peak shape.
   %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.
+
   As a baseline, we created a simplified model using the same amount of disorder present
@@
   early equilibration and is locked into place for the remainder of the simulation time. The
-  latter has important implications for the reproducibility of this work since velocity
-  randomization at the beginning of equilibration will result in different quenched 
-  configurations. 
-  %MRS9: could be that initial starting configurations would ALSO give rise to different quenched configurations.
-We measured thermal disorder by measuring the standard deviation in
-  the distribution of head group center of mass positions from their average positions.
-  We measured quenched disorder by calculating the standard deviation of the distribution 
-  of head group center of masses from their 
-%ideal positions. 
-idealized average positions.
-In the $z$-direction, we measured
-  the deviation of the head group center of masses from an equally spaced column of head groups.
-  In the $xy$ plane, we calculated the deviation in radial position from the pore center and 
-  the angular deviation from equally spaced points surrounding the pore center. The values
-  measured for each system are given in Table~\ref{table:quenched_disorder}. We built a simple
-  system consisting of 1000 independent configurations using these parameters. We also made
-  the simple system 4 times taller in order to get better resolution in the $q_z$ direction. 
-  Figure~\ref{fig:sf_qy_nocorrelation} shows the $q_y$ cross-section of R-$\pi$ generated by
-  simulating the structure factor of the trajectory.
-
-  %BJC8: Need to add thermal noise to this table
+  latter has important implications for the reproducibility of this work since both initial
+  configurations and velocity randomization at the beginning of equilibration can lead to
+  different quenched configurations. We measured thermal disorder by measuring the standard 
+  deviation in the distribution of head group center of mass positions from their average 
+  positions. We measured quenched disorder by calculating the standard deviation of the 
+  distribution of head group center of masses from their idealized average positions. In the
+  $z$-direction, we measured the deviation of the head group center of masses from an equally
+  spaced column of head groups. In the $xy$ plane, we calculated the deviation in radial 
+  position from the pore center and the angular deviation from equally spaced points surrounding
+  the pore center. The values measured for each system are given in Table~\ref{table:quenched_disorder}.
+  Using these parameters, we built a trajectory consisting of 1000 independent configurations. 
+  We also made the simple system 4 times taller in order to get better resolution in the $q_z$ 
+  direction. Figure~\ref{fig:sf_qy_nocorrelation} shows the $q_y$ cross-section of R-$\pi$ 
+  generated by simulating the structure factor of the trajectory.
+
   \begin{table}[h]
   \centering
-  \begin{tabular}{c|ccc}
+  \begin{tabular}{c|ccc|ccc}
   \toprule
-  System                        & $\sigma_z$ ($\AA$) & $\sigma_\theta$ (rad) & $\sigma_r$ ($\AA$) \\
+   		                        &           \multicolumn{3}{c}{Thermal Disorder}             &             \multicolumn{3}{c}{Quenched Disorder}               \\
   \midrule
-  Ordered Sandwiched            &        1.48        &     0.43              &     2.30           \\
-  Ordered Parallel Displaced    &        1.45        &     0.43              &     2.28           \\ 
-  Disordered Sandwiched         &        1.58        &     0.43              &     2.93           \\
-  Disordered Parallel Displaced &        1.65        &     0.43              &     2.63           \\
+  System                        & $\sigma_x$ ($\AA$) & $\sigma_y$ (rad) & $\sigma_z$ ($\AA$) & $\sigma_z$ ($\AA$) & $\sigma_\theta$ (rad) & $\sigma_r$ ($\AA$) \\
+  \midrule
+  Ordered Sandwiched            &         0.31       &       0.33       &        0.34        &        1.48        &     0.43              &     2.30           \\
+  Ordered Parallel Displaced    &         0.51       &       0.52       &        0.30        &        1.45        &     0.43              &     2.28           \\ 
+  Disordered Sandwiched         &         0.41       &       0.57       &        0.32        &        1.58        &     0.43              &     2.93           \\
+  Disordered Parallel Displaced &         0.39       &       0.31       &        0.33        &        1.65        &     0.43              &     2.63           \\
   \bottomrule
   \end{tabular}
-  %MRS9: tweaked
-  \caption{Deviation of the positions of the center of mass of head groups from
-  idealized positions to use as simulated disorder into our model system.}
+  \caption{Deviation of the positions of the center of mass of head groups from their average
+  positions (Thermal Disorder) as well as their idealized positions (Quenched Disorder) to use 
+  as simulated disorder into our model system.}
   \label{table:quenched_disorder} 
@@
   %MRS9: better to say ``data is most consistent with the idea that the real configuration is somewhere between''
-%  There is no major difference between R-$\pi$ of a parallel displaced system and a 
-%  sandwiched system.
-%  \begin{itemize}
-%  	\item Intensity does not change
-%  	\item 
-%  \begin{itemize}
 
 %MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
+%BJC9: haha^
+%BJC9: I could probably get rid of qy cross-sections and inset in (c)
   \begin{figure}[!htb]
@@
   R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
-  %MRS9: in c, weird that the orange peaks are broader, but taller. Not sure I understand. 
+  % MRS9: in c, weird that the orange peaks are broader, but taller. Not sure I understand.
+  % BJC9: Good catch, not sure why I didn't question that. Was inputting square root of standard deviation 
+  % rather than square of standard deviation as variance, so there was less noise. Fixed now.
+  % BJC9: Heights are still slightly different after 1000 independent configurations
+  % BJC9: Shape is also different. Looks like the points are more evenly spaced in correlated
+  % system so there are less points at high and low q.
   \end{figure}
@@
   other. To remedy this, we randomly sampled a multivariate normal distribution
-  with the same 
-  %variance, v, 
-  standard deviation, $\sigma$.
-  implied by Table~\ref{table:quenched_disorder}. We 
-  defined the distribution using a covariance matrix such that the covariance
+  with the same standard deviation, $\sigma$ shown in by Table~\ref{table:quenched_disorder}. We 
+  defined the distribution using a covariance matrix such that the covariance, v,
   in position, z, between scatterers decays exponentially from v according to the
@@
   The distance between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all 
-  cases,
-  %MRS9: added
-  with disordered basins at the high part of that range 0.2 and 0.3 \AA~more distant.
+  cases, with disordered basins at the high part of that range, 0.2 and 0.3 \AA~more distant.
   %MRS9: GAFF could OVER predict pi-pi stacking, best to include citations here that it does indeed overpredict.
+  %BJC9: Turns out the Jankowski group was using oplsaa, not GAFF (they said GAFF to me). Will search for other
+  % references.
   This behavior is not surprising since GAFF models atoms as point charges and does not 
   appropriately model the aromatic $\pi-\pi$ interactions which would make it more energetically
-  favorable for the monomers to stack closer together. 
-Additionally, it is possible that the 
+  favorable for the monomers to stack closer together. Additionally, it is possible that the 
   tails prevent close stacking of monomer head groups and we do not achieve the timescales 
-  necessary for them to rearrange into a necessarily more tightly packed configuration. Ordered
-  basin systems are likely the best choice for transport studies. 
-%MRS9: make it clearer if the last sentence is a conclusion based on the other evidence in the paragraph.
+  necessary for them to rearrange into a necessarily more tightly packed configuration. Since 
+  ordered basin systems pack closest together, they are likely the best choice for transport 
+  studies.
 
@@
 
-  Increased thermal noise in the z-direction causes a drop in the intensity of R-$\pi$, however 
-  the $q_r$ profile remains unchanged. 
-  \begin{itemize}
-  	\item Show how I can decrease the intensity by a factor of 3-15 x by just increasing z-direction
-  	thermal noise
-  	\item Can put thermal noise vs. intensity in supporting info.
-  	\item The peaks are still sharp though
-  	\item 3 panel figure : regular intensity, 3x decrease, 15x decrease. Peak shapes all the same
-  \end{itemize}
+  Increased thermal noise in the $z$-direction causes a drop in the intensity of R-$\pi$, however 
+  the $q_r$ profile remains unchanged. When we increase the thermal noise in the $z$-direction by
+  11\% and 28\%, we see a 3 and 15 fold decrease in the intensity of R-$\pi$ respectively (Figure
+  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections have the same shape,
+  whose sharp Bragg-like peaks are not consistent with experiment. The peaks are spaced apart
+  according to the pore spacing, and line up with R-alkanes. The center of mass of all columns in
+  our initial configuration are situated at the z coordinate.
+
+  % BJC9: could overlay these plots, but might look messy. Maybe there is a more compact representation
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qy_correlation.png}  %BJC9: z_variance = 2.074 angstroms
+  \caption{}\label{fig:sf_znoise_control}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qy_3xdecrease.png}  %BJC9: z_variance = 2.55 angstroms
+  \caption{}\label{fig:3xdecrease}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qy_15xdecrease.png}  %BJC9: z_variance = 3.4 angstroms
+  \caption{}\label{fig:15xdecrease}
+  \end{subfigure}
+  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
+  however the $q_r$ cross-section profile does not change. (a) The maximum intensity of R-$\pi$ is ca. 20 
+  when we use the same level of noise present in the atomistic simulation. (b) The intensity of R-$\pi$ 
+  decreases by a factor of 3, relative to the background intensity, if we increase thermal noise by 11\% 
+  in the $z$-direction. (c) The intensity of R-$\pi$ decreases by a factor of 15, relative to the background
+  intensity, when we increase thermal noise by 28\% in the $z$-direction.}\label{fig:znoise}
+  \end{figure}
 
@@
   of R-$\pi$ drops and the $q_r$ cross-section of the simulated diffraction patterns 
-  smooths out.
-  \begin{itemize}
-  	\item Allowing columns to move independently smooths out the $q_r$ cross-section. Any amount
-  	of dependence results in sharp peaks.
-  	\item R-$\pi$ intensity decreases by up to 10x
-  	\item Can put R-$\pi$ intensity vs. column independence in supporting info.
-  	\item Predict level of independence in simulation (what amount of displacement cause the 
-  	R-$\pi$ profile to look like that shown in Figure 8d). %MRS9: this is a bit complicated, since it could be a combination of factors.
-  	\item Figure: (a) x \% column displacement give Figure 8d (b) Independent columns give a smooth
-  	curve %MRS9: not quite sure what you are talking about in this figure.  Could you give more information?
-  \end{itemize}
-
-  Increasing thermal noise in the x and y directions causes R-$\pi$ to sharpen in the 
-  $q_r$ direction. %MRS9: this is unanticiated (noise creating sharpening) so will have to make it clear.
+  smooths out. We created simple systems with varying amounts of association between columns. 
+  In the low limit, the center of mass of columns are situated at the same z coordinate. 
+  This is how all simple systems have been created up to this point. We allow increasing 
+  independence of columns by randomly shifting each column in the $z$-direction using a uniform
+  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ is between 0 and 1. We
+  limit this discussion to configurations close to a sandwiched configuration since it is not
+  feasible for columns in the parallel displaced configuration, as we have set them up, to move
+  past each other. Allowing columns to move independently smooths out the $q_r$ cross-section
+  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp peaks. The
+  intensity of R-$\pi$ decreases with increasing column independence. We see an 8 fold decrease
+  in the intensity of R-$\pi$ when $f=1$ versus when $f=0$.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qy_sr0.png}
+  \caption{$f$ = 0}\label{fig:sf_qy_sr0}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qy_sr75.png}
+  \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{sf_qy_sr100.png}
+  \caption{$f$ = 1}\label{fig:sf_qy_sr100}
+  \end{subfigure}
+  \caption{As we increase column independence using the $f$ parameter, the intensity of R-$\pi$
+  decreases and the $q_r$ cross-section of the simulated diffraction pattern becomes more smooth.
+  (a) When we place all columns at the same z coordinate, $f$ = 0, the intensity of R-$\pi$ is
+  18.3 and is characterized by sharp Bragg-like peaks. (b) When columns have a moderate amount of
+  independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold to 3.7. The edges of the
+  peak are beginning to smooth out, but sharp peaks still exist. (c) When columns are completely
+  independent, $f$ = 1, the intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
+  relatively smooth.}\label{fig:column_displacement}
+  \end{figure}
+
+  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$ cross-section of R-$\pi$
+  to decrease.
   \begin{itemize}
@@
   \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
+  \caption{}\label{fig:qy_fwhm}
+  \end{figure}
 
@@
 
-  The system size 
-  %MRS9: added
-  in the $z$-direction.
-  does not significantly alter the intensity of R-$\pi$. We equilibrated a 
+  The system size in the $z$-direction does not significantly alter the intensity of R-$\pi$. We equilibrated a 
   sandwiched system with twice as many monomers per column so that the system size doubled in 

### 2018-08-08 Ben_Manuscripts/structure_paper/Draft.tex
new figures

@@
   The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections of R-$\pi$ 
-  are in moderate agreement with experiment (Figure~\ref{fig:rpi_exp_comparison}). The
+  are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}). The
   FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the $q_r$ cross-section
@@
   function while the simulated patterns are best fit using a Gaussian function. The simulated
-  spectra do not incorporate the effects of pressure broadening and instrumental broadening
+  spectra do not incorporate the effects of finite domain sizes, pressure broadening and instrumental broadening
   which would alter the peak shape. In the absence of these and other peak broadening effects,
@@
 FWHM is a natural scale parameter for Lorenzians, but not really for Gaussian.
+
   \begin{figure}
@@
 
-  %MRS9: Could be stronger thesis.  Suggest
   We have identified a number of potential ways that simulation conditions, forcefield 
-  and initial configurations could affect the intensity of R-$\pi$ as well its FWHM in 
+  and initial configurations could affect the intensity of R-$\pi$ as well as its FWHM in 
   the $q_z$ and $q_r$ directions. We assessed each using a simplified model. Our 
@@
   in either a parallel displaced or sandwiched configuration. We chose to explore
-  the influence of thermal noise in each dimension, correlation between scatterers within
-  columns, as well as correlation between columns since these are the variables we 
-  believe have the largest influence on peak shape.
+  the influence of thermal noise in each dimension, the effect of $z$-direction distance correlations
+  between scatterers within columns, as well as correlation between columns since these are the variables we 
+  believe have the largest influence on peak shape and intensity.
   %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.
@@
   atoms and quenched disorder which is created by rapid structural rearrangement during
-  early equilibration and is locked into place for the remainder of the simulation time. The
+  early equilibration and is largely locked into place for the remainder of the simulation. The
   latter has important implications for the reproducibility of this work since both initial
   configurations and velocity randomization at the beginning of equilibration can lead to
-  different quenched configurations. We measured thermal disorder by measuring the standard 
-  deviation in the distribution of head group center of mass positions from their average 
+  different quenched configurations. We measured thermal disorder by calculating the standard 
+  deviation of the distribution of head group center of mass positions from their average 
   positions. We measured quenched disorder by calculating the standard deviation of the 
@@
   position from the pore center and the angular deviation from equally spaced points surrounding
-  the pore center. The values measured for each system are given in Table~\ref{table:quenched_disorder}.
-  Using these parameters, we built a trajectory consisting of 1000 independent configurations. 
-  We also made the simple system 4 times taller in order to get better resolution in the $q_z$ 
-  direction. Figure~\ref{fig:sf_qy_nocorrelation} shows the $q_y$ cross-section of R-$\pi$ 
-  generated by simulating the structure factor of the trajectory.
+  the pore center. The values measured for each system and type of disorder are given in 
+  Table~\ref{table:quenched_disorder}.
+
+  The intensity of R-$\pi$ can be calculated from a single trajectory of uncorrelated
+  configurations rather than as the average of multiple correlated trajectories. Theoretically,
+  in order to mimic the simulated system, we should build an initial configuration which 
+  has the same amount of quenched disorder as our simulations and then create a trajectory
+  to which we add thermal disorder to the initial configuration in order to create each frame.
+  %BJC9 : The following numbers need to be updated: I want to do 40 trajectories with 1000 frames each for both types of trajectories and compare their mean and uncertainty
+  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this way was 
+  16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000 initial configurations,
+  the intensity of R-$\pi$ is 16.42, in close agreement with the mean of 40 simulations. 
+  We use the latter method for the remainder of this work since we can extract the trends
+  we need using a single trajectory at a fraction of the computational cost.
+
+  When we simulated the diffraction pattern of a simple system trajectory of 1000 independent
+  configurations, each created using the parameters for thermal and quenched disorder in order to place 
+  points, the $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
+  this simple system, and all to follow, 4 times taller in the $z$-direction in order to access
+  higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation} and~\ref{fig:sf_qz_correlation}
+  shows the $q_y$ and $q_z$ cross-sections of R-$\pi$ generated by simulating the structure 
+  factor of the trajectory. The distance between peaks in the $q_y$ cross-section is equal
+  to the distance between pores in real space.
 
@@
   \includegraphics[width=\textwidth]{sf_qy_correlation.png}
-  \caption{}\label{fig:sf_qy_correlation.png}
+  \caption{}\label{fig:sf_qy_correlation}
   \end{subfigure} 
@@
   \includegraphics[width=\textwidth]{sf_qz_correlation.png}
-  \caption{}\label{fig:sf_qz_correlation.png}
+  \caption{}\label{fig:sf_qz_correlation}
   \end{subfigure}   
@@
   $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
-  peaks. (b) When we make points in each column correlated, the intensity of R-$\pi$ 
-  increases but the sharp peaks remain with the same ratio of intensity between the
-  center and outer peaks. (c) 
-  %MRS9: I'm not sure what you mean by ``correlation'' broadening peaks here.  Do you mean replacing exact periodicity by 
-  %correlated random points  Because that reduces correlation (from 100% to less than 100%).
-Correlation between scatterers in the $z$-direction causes
-  R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
-  % MRS9: in c, weird that the orange peaks are broader, but taller. Not sure I understand.
-  % BJC9: Good catch, not sure why I didn't question that. Was inputting square root of standard deviation 
-  % rather than square of standard deviation as variance, so there was less noise. Fixed now.
-  % BJC9: Heights are still slightly different after 1000 independent configurations
-  % BJC9: Shape is also different. Looks like the points are more evenly spaced in correlated
-  % system so there are less points at high and low q.
+  peaks. (b) When we correlate the distance between points within each column, the 
+  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
+  intensity between the center and outer peaks. (c) Correlation of the distance between
+  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
   \end{figure}
 
-  Scatterers in each column are correlated with each other. In the simplified 
-  system described above, we added uncorrelated Gaussian noise in the 
-  z-direction which ignores any interaction head groups might have with each
-  other. To remedy this, we randomly sampled a multivariate normal distribution
-  with the same standard deviation, $\sigma$ shown in by Table~\ref{table:quenched_disorder}. We 
-  defined the distribution using a covariance matrix such that the covariance, v,
-  in position, z, between scatterers decays exponentially from v according to the
-  equation $ve^{-z/L}$, where L is the correlation length. Experimentally, the
-  correlation length can be estimated as the inverse of the FWHM of the $q_z$
-  cross-section of R-$\pi$.  %BJC8: needs references 
+  The distances between scatterers within each column are correlated with each other.
+  In the simplified system described above, we added Gaussian noise to the 
+  mean positions of an equally spaced column of points. This ignores any interaction
+  head groups might have with each other. To remedy this, we drew random samples from 
+  a multivariate normal distribution defined by the mean positions of an equally spaced
+  column of points. We gave the distribution at each point along the column the same
+  standard deviation, $\sigma_z$, shown  in by Table~\ref{table:quenched_disorder}. We 
+  defined a covariance matrix such that the covariance, v, in the distance, z, between
+  scatterers decays exponentially from v according to the equation $ve^{-z/L}$, where L
+  is the correlation length. Experimentally, the correlation length can be estimated as
+  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$.  %BJC8: needs references 
   Accordingly, the correlation length of the experimental system is $\geq$ 9 
   $\AA$. The value may be larger since the peak is likely broadened for a variety
-  of other reasons. %BJC8: the reasons I can provide more detail on above.  
+  of other reasons. We simulated the structure factor of a simple system built as described
+  above with a correlation length of 30 $\AA$. We chose 30 $\AA$ in order to exaggerate
+  the effect of correlation length for visual purposes. Subsequent structure factor calculations
+  are all done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section 
+  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$ cross-section
+  (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in experiment. Additionally, there
+  is a near 20 \% increase in the maximum intensity of R-$\pi$ when the distances between
+  scatterers are correlated.
+
   %BJC8: Can show correlation effect on intensity in supporting info
@@
   the $q_r$ profile remains unchanged. When we increase the thermal noise in the $z$-direction by
-  11\% and 28\%, we see a 3 and 15 fold decrease in the intensity of R-$\pi$ respectively (Figure
-  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections have the same shape,
-  whose sharp Bragg-like peaks are not consistent with experiment. The peaks are spaced apart
-  according to the pore spacing, and line up with R-alkanes. The center of mass of all columns in
-  our initial configuration are situated at the z coordinate.
-
-  % BJC9: could overlay these plots, but might look messy. Maybe there is a more compact representation
+  12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of R-$\pi$ respectively (Figure
+  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections have the same shape
+  (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp Bragg-like peaks are not consistent with 
+  experiment.
+
+  % BJC9: Might be worth acknowledging:
+  % The peaks are spaced apart according to the pore spacing, and line up with R-alkanes.
+
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.3\textwidth}
+%  \includegraphics[width=\textwidth]{sf_qy_correlation_L10.png}  %BJC9: z_variance = 2.074 angstroms
+%  \caption{}\label{fig:sf_znoise_control}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\textwidth}
+%  \includegraphics[width=\textwidth]{sf_qy_3xdecrease.png}  %BJC9: z_variance = 2.65 angstroms
+%  \caption{}\label{fig:3xdecrease}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\textwidth}
+%  \includegraphics[width=\textwidth]{sf_qy_15xdecrease.png}  %BJC9: z_variance = 3.4 angstroms
+%  \caption{}\label{fig:15xdecrease}
+%  \end{subfigure}
+%  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
+%  however the $q_r$ cross-section profile does not change. (a) The maximum intensity of R-$\pi$ is ca. 20 
+%  when we use the same level of noise present in the atomistic simulation. (b) The intensity of R-$\pi$ 
+%  decreases by a factor of 3, relative to the background intensity, if we increase thermal noise by 11\% 
+%  in the $z$-direction. (c) The intensity of R-$\pi$ decreases by a factor of 15, relative to the background
+%  intensity, when we increase thermal noise by 28\% in the $z$-direction.}\label{fig:znoise}
+%  \end{figure}
+
   \begin{figure}[!htb]
   \centering
-  \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qy_correlation.png}  %BJC9: z_variance = 2.074 angstroms
-  \caption{}\label{fig:sf_znoise_control}
-  \end{subfigure}
-  \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qy_3xdecrease.png}  %BJC9: z_variance = 2.55 angstroms
-  \caption{}\label{fig:3xdecrease}
-  \end{subfigure}
-  \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qy_15xdecrease.png}  %BJC9: z_variance = 3.4 angstroms
-  \caption{}\label{fig:15xdecrease}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
+  \caption{}\label{fig:intensity_vs_zsigma}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
+  \caption{}\label{fig:rpi_xsection_vs_zsigma}
   \end{subfigure}
   \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
-  however the $q_r$ cross-section profile does not change. (a) The maximum intensity of R-$\pi$ is ca. 20 
-  when we use the same level of noise present in the atomistic simulation. (b) The intensity of R-$\pi$ 
-  decreases by a factor of 3, relative to the background intensity, if we increase thermal noise by 11\% 
-  in the $z$-direction. (c) The intensity of R-$\pi$ decreases by a factor of 15, relative to the background
-  intensity, when we increase thermal noise by 28\% in the $z$-direction.}\label{fig:znoise}
+  however the $q_r$ cross-section profile does not change. (a) The intensity of R-$\pi$ drops precipitously
+  as we increase $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the background intensity
+  as seen in our simulation (blue) by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase 
+  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$ decreases with increasing $\sigma_z$,
+  the peak shape remains the same.}\label{fig:znoise}
   \end{figure}
@@
   smooths out. We created simple systems with varying amounts of association between columns. 
-  In the low limit, the center of mass of columns are situated at the same z coordinate. 
+  In the low limit, the center of mass of columns are situated at the same $z$-coordinate. 
   This is how all simple systems have been created up to this point. We allow increasing 
   independence of columns by randomly shifting each column in the $z$-direction using a uniform
-  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ is between 0 and 1. We
-  limit this discussion to configurations close to a sandwiched configuration since it is not
+  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We
+  limit this discussion to the sandwiched configuration since it is not
   feasible for columns in the parallel displaced configuration, as we have set them up, to move
-  past each other. Allowing columns to move independently smooths out the $q_r$ cross-section
+  past each other. The trends seen above apply to both the sandwiched and parallel displaced systems.
+  Allowing columns to move independently smooths out the $q_r$ cross-section
   (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp peaks. The
-  intensity of R-$\pi$ decreases with increasing column independence. We see an 8 fold decrease
+  intensity of R-$\pi$ decreases with increasing column independence. We see an 8-fold decrease
   in the intensity of R-$\pi$ when $f=1$ versus when $f=0$.
@@
 
-  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$ cross-section of R-$\pi$
-  to decrease.
-  \begin{itemize}
-    \item $q_r$ cross-section still too broad
-    \item Adding more thermal noise sharpens it
-    \item Figure: Overlay thinner FWHM plot on top of wider FWHM 
-  \end{itemize}
+  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$ cross-section of 
+  R-$\pi$ to decrease. We modified the disorder in both the $r$ and $\theta$ directions by
+  multiplying their values by a factor of 0.5 and 2 (Figure~\ref{fig:qy_fwhm}). When we cut
+  the noise in half, the FWHM increases by 88 \%. When we double the noise, the FWHM 
+  decreases by 51 \%.
 
@@
   \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
-  \caption{}\label{fig:qy_fwhm}
+  \caption{Increasing the amount of disorder in the $xy$ plane decreases the FWHM of the 
+  $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and $theta$ disorder in
+  half (Noise factor = 0.5), the FWHM increases by 88\%. When we double the disorder 
+  (Noise factor = 2), the FWHM decreases by 51\%.}\label{fig:qy_fwhm}
   \end{figure}
 
-%MRS9: the statement below is pretty strong, need to back it up.  We know that we have quenched noise, which is a type of over-ordering - is that taken into account?  
-  We have nearly the right amount of disorder / noise in our system, but correlation 
-  between columns really messes up R-$\pi$.
+  We can use what we learned above in order to construct a better model, however there
+  will still be shortcomings. We can decrease the intensity of R-$\pi$ if we incorporate
+  more $z$-directional noise, which may come from increasing the system's temperature.
+  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
+  % temperature? Is decreasing the force constant between bonds viable? 
+  We can adjust the parameters for aromatic carbons so that head groups stack more 
+  closely together. Perhaps the simplest thing to do is to create initial configurations
+  whose columns are displaced randomly in the $z$-direction in order to mimic independence.
+  Ultimately, we will need extremely long simulation times so that monomers within 
+  columns can rearrange and sample enough independent configurations to generate a robust
+  simulated XRD pattern.
+
+  The architecture of each column is likely somewhere between sandwiched and parallel 
+  displaced. The parallel displaced configuration that we have simulated in this paper
+  is an exaggerated manifestation of the parallel displaced $\pi-\pi$ stacking mode. 
+  The simulated XRD pattern shows faint off-axis features at the same $q_r$ value as
+  R-double which is only in patterns generated from parallel displaced configurations. 
+  The monomers may prefer to be parallel displaced, but their displacement is likely 
+  only slightly shifted, on the $xy$ plane, from the center of mass of their vertically
+  adjacent neighbors. In this way, columns can more easily act independently while 
+  maintaining a parallel displaced structure.
 

### 2018-08-08 Ben_Manuscripts/structure_paper/Draft.tex
Updates

@@
 
-  Evidence strongly suggests that the R-spots signal is not a result of alkane chain tilt. 
-  Previous literature has attributed the spots in this particular WAXS pattern as the product 
-  of tilted alkane chains~\cite{feng_scalable_2014}. We measured the tilt angle of the
-  alkane chains of the 280K system and showed that it equilibrates to an average tilt angle of
-  -2\degree (Fig.~\ref{fig:tilt}), far from the 37\degree tilt angle previously used to 
-  explain R-spots. 
+  Evidence strongly suggests that the R-spots signal is not a result of alkane
+  chain tilt.  Previous literature has attributed the spots in this particular
+  WAXS pattern as the product of tilted alkane chains~\cite{feng_scalable_2014}.
+  We measured the tilt angle of the alkane chains of the 280K system and showed
+  that it equilibrates to an average tilt angle of
+  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
+  used to explain R-spots. 
   %MRS8: did you do a few different things here as sensitivity analysis to show that the finding was robust?  If so, putting some of that in would be useful.
@@
 
-  To understand the most likely origin of R-spots, we determined which atoms
-  gave rise to the feature. 
-  %MRS8: next two sentences repetitive; could you revise? 
-%  Since R-spots is present as higher intensity spots within R-alkanes, it is
-%  likely that the spots arise as a consequence of the tails. 
-  By removing all non-tail atoms from the trajectory and simulating a
-  diffraction pattern with the remaining atoms, we were able to isolate the cause
-  of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the tails stay
-  nearly flat, we plotted their centroids (Figure \ref{fig:centroids}) and
-  measured the angle between each centroid and its nearest neighbors with respect
-  to the plane of the membrane. We see distinct peaks in the distribution of
-  these angles (Figure~\ref{fig:tail_packing}).
+  R-spots originates from the monomer tails.
+  %To understand the most likely origin of R-spots, we determined which atoms
+  %gave rise to the feature. 
+  By removing all non-tail atoms from the trajectory
+  and simulating a diffraction pattern with the remaining atoms, we were able to
+  isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
+
+  The tails pack together hexagonally. Since the tails stay nearly flat, we plotted
+  their centroids (Figure \ref{fig:centroids}) and measured the angle between
+  each centroid and its nearest neighbors with respect to the plane of the
+  membrane. We see distinct peaks in the distribution of these angles which are
+  consistent with a hexagonally packed configuration
+  (Figure~\ref{fig:tail_packing}).
 
@@
         \centering
-	        \includegraphics[width=\linewidth]{angles_traj_layered.png}
+	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.png}
 	        \caption{}~\label{fig:layered_tails}
@@
 
-  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections of R-$\pi$ 
-  are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}). The
-  FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the $q_r$ cross-section
-  FWHM is 21\% larger than experiment. Note that the experimental data is best fit with a Lorentzian 
-  function while the simulated patterns are best fit using a Gaussian function. The simulated
-  spectra do not incorporate the effects of finite domain sizes, pressure broadening and instrumental broadening
-  which would alter the peak shape. In the absence of these and other peak broadening effects,
-  the experimental peak would actually be narrower, further increasing the discrepancy with simulation.
+  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
+  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
+  The FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the
+  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
+  experimental data is best fit with a Lorentzian function while the simulated
+  patterns are best fit using a Gaussian function. The simulated spectra do not
+  incorporate the effects of finite domain sizes, pressure broadening and
+  instrumental broadening which would alter the peak shape. In the absence of
+  these and other peak broadening effects, the experimental peak would actually
+  be narrower, further increasing the discrepancy with simulation.
 
@@
   \caption{
-  In experiments ((a) and (b)), (a), R-$\pi$ broadens in the $q_z$ direction with a FWHM of 
-  0.110 $\pm$ 0.003 $\AA^{-1}$ when fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
-  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. In our simulations ((c) and (d)), (c) the FWHM of R-$\pi$ in
-  the $q_z$ direction is 0.194 $\pm$ 0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width
-  of experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01 $\AA^{-1}$ when fit with
-  a Gaussian function, about 20 \% larger than experiment. Note that the large spike in the center is not included
-  in the fit.}\label{fig:rpi_exp_comparison}
+  In experiments ((a) and (b)), (a), R-$\pi$ broadens in the $q_z$ direction
+  with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when fit with a Lorentzian
+  function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792
+  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. In our simulations
+  ((c) and (d)), (c) the FWHM of R-$\pi$ in the $q_z$ direction is 0.194 $\pm$
+  0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width of
+  experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01
+  $\AA^{-1}$ when fit with a Gaussian function, about 20 \% larger than
+  experiment. Note that the large spike in the center is not included in the
+  fit.}\label{fig:rpi_exp_comparison}
   \end{figure}
 
-  We have identified a number of potential ways that simulation conditions, forcefield 
-  and initial configurations could affect the intensity of R-$\pi$ as well as its FWHM in 
-  the $q_z$ and $q_r$ directions. We assessed each using a simplified model. Our 
-  simplified model represents each monomer head group as a single point and places them
-  in either a parallel displaced or sandwiched configuration. We chose to explore
-  the influence of thermal noise in each dimension, the effect of $z$-direction distance correlations
-  between scatterers within columns, as well as correlation between columns since these are the variables we 
-  believe have the largest influence on peak shape and intensity.
+  We have identified a number of potential ways that simulation conditions,
+  forcefield and initial configurations could affect the intensity of R-$\pi$ as
+  well as its FWHM in the $q_z$ and $q_r$ directions. We assessed each using a
+  simplified model. Our simplified model represents each monomer head group as a
+  single point and places them in either a parallel displaced or sandwiched
+  configuration. We chose to explore the influence of thermal noise in each
+  dimension, the effect of $z$-direction distance correlations between scatterers
+  within columns, as well as correlation between columns since these are the
+  variables we believe have the largest influence on peak shape and intensity.
   %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.
 
-  As a baseline, we created a simplified model using the same amount of disorder present
-  in our atomistic simulations. There are two sources of disorder to consider: thermal motion of
-  atoms and quenched disorder which is created by rapid structural rearrangement during
-  early equilibration and is largely locked into place for the remainder of the simulation. The
-  latter has important implications for the reproducibility of this work since both initial
-  configurations and velocity randomization at the beginning of equilibration can lead to
-  different quenched configurations. We measured thermal disorder by calculating the standard 
-  deviation of the distribution of head group center of mass positions from their average 
-  positions. We measured quenched disorder by calculating the standard deviation of the 
-  distribution of head group center of masses from their idealized average positions. In the
-  $z$-direction, we measured the deviation of the head group center of masses from an equally
-  spaced column of head groups. In the $xy$ plane, we calculated the deviation in radial 
-  position from the pore center and the angular deviation from equally spaced points surrounding
-  the pore center. The values measured for each system and type of disorder are given in 
-  Table~\ref{table:quenched_disorder}.
-
-  The intensity of R-$\pi$ can be calculated from a single trajectory of uncorrelated
-  configurations rather than as the average of multiple correlated trajectories. Theoretically,
-  in order to mimic the simulated system, we should build an initial configuration which 
-  has the same amount of quenched disorder as our simulations and then create a trajectory
-  to which we add thermal disorder to the initial configuration in order to create each frame.
+  As a baseline, we created a simplified model using the same amount of
+  disorder present in our atomistic simulations. There are two sources of
+  disorder to consider: thermal motion of atoms and quenched disorder which is
+  created by rapid structural rearrangement during early equilibration and is
+  largely locked into place for the remainder of the simulation. The latter has
+  important implications for the reproducibility of this work since both initial
+  configurations and velocity randomization at the beginning of equilibration can
+  lead to different quenched configurations. We measured thermal disorder by
+  calculating the standard deviation of the distribution of head group center of
+  mass positions from their average positions. We measured quenched disorder by
+  calculating the standard deviation of the distribution of head group center of
+  masses from their idealized average positions. In the $z$-direction, we
+  measured the deviation of the head group center of masses from an equally
+  spaced column of head groups. In the $xy$ plane, we calculated the deviation in
+  radial position from the pore center and the angular deviation from equally
+  spaced points surrounding the pore center. The values measured for each system
+  and type of disorder are given in Table~\ref{table:quenched_disorder}.
+
+  The intensity of R-$\pi$ can be calculated from a single trajectory of
+  uncorrelated configurations rather than from the average of multiple correlated
+  trajectories. Theoretically, in order to mimic the simulated system, we should
+  build an initial configuration which has the same amount of quenched disorder
+  as our simulations and then create a trajectory to which we add thermal
+  disorder to the initial configuration in order to create each frame.
   %BJC9 : The following numbers need to be updated: I want to do 40 trajectories with 1000 frames each for both types of trajectories and compare their mean and uncertainty
-  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this way was 
-  16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000 initial configurations,
-  the intensity of R-$\pi$ is 16.42, in close agreement with the mean of 40 simulations. 
-  We use the latter method for the remainder of this work since we can extract the trends
-  we need using a single trajectory at a fraction of the computational cost.
-
-  When we simulated the diffraction pattern of a simple system trajectory of 1000 independent
-  configurations, each created using the parameters for thermal and quenched disorder in order to place 
-  points, the $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
-  this simple system, and all to follow, 4 times taller in the $z$-direction in order to access
-  higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation} and~\ref{fig:sf_qz_correlation}
-  shows the $q_y$ and $q_z$ cross-sections of R-$\pi$ generated by simulating the structure 
-  factor of the trajectory. The distance between peaks in the $q_y$ cross-section is equal
-  to the distance between pores in real space.
+  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this
+  way was 16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000
+  initial configurations, the intensity of R-$\pi$ is 16.42, in close agreement
+  with the mean of 40 simulations.  We use the latter method for the remainder of
+  this work since we can extract the trends we need using a single trajectory at
+  a fraction of the computational cost.
+
+  When we simulated the diffraction pattern of a parallel displaced simple
+  system trajectory of 1000 independent configurations, each created using the
+  parameters for thermal and quenched disorder in order to place points, the
+  $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
+  this simple system, and all to follow, 4 times taller in the $z$-direction in
+  order to access higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation}
+  and~\ref{fig:sf_qz_correlation} shows the $q_y$ and $q_z$ cross-sections of
+  R-$\pi$ generated by simulating the structure factor of the trajectory. The
+  distance between peaks in the $q_y$ cross-section is equivalent to the distance
+  between pores in real space.
 
@@
 
-  %BJC8: Create parallel displaced configuration: create sandwiched system. Apply uniform rotation to every other layer
-  %BJC8: I'd like to make the point somewhere that the real configuration is somewhere between sandwiched and the
-  % parallel displaced configuration shown here.
-  %MRS9: better to say ``data is most consistent with the idea that the real configuration is somewhere between''
-
 %MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
-%BJC9: haha^
-%BJC9: I could probably get rid of qy cross-sections and inset in (c)
+%BJC9: hahaha^
   \begin{figure}[!htb]
@@
 
-  The distances between scatterers within each column are correlated with each other.
-  In the simplified system described above, we added Gaussian noise to the 
-  mean positions of an equally spaced column of points. This ignores any interaction
-  head groups might have with each other. To remedy this, we drew random samples from 
-  a multivariate normal distribution defined by the mean positions of an equally spaced
-  column of points. We gave the distribution at each point along the column the same
-  standard deviation, $\sigma_z$, shown  in by Table~\ref{table:quenched_disorder}. We 
-  defined a covariance matrix such that the covariance, v, in the distance, z, between
-  scatterers decays exponentially from v according to the equation $ve^{-z/L}$, where L
-  is the correlation length. Experimentally, the correlation length can be estimated as
-  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$.  %BJC8: needs references 
-  Accordingly, the correlation length of the experimental system is $\geq$ 9 
-  $\AA$. The value may be larger since the peak is likely broadened for a variety
-  of other reasons. We simulated the structure factor of a simple system built as described
-  above with a correlation length of 30 $\AA$. We chose 30 $\AA$ in order to exaggerate
-  the effect of correlation length for visual purposes. Subsequent structure factor calculations
-  are all done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section 
-  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$ cross-section
-  (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in experiment. Additionally, there
-  is a near 20 \% increase in the maximum intensity of R-$\pi$ when the distances between
-  scatterers are correlated.
+  The distances between scatterers within each column are correlated with each
+  other. In the simplified system described above, we added Gaussian noise to
+  the mean positions of an equally spaced column of points. This ignores any
+  interaction head groups might have with each other. To remedy this, we drew
+  random samples from a multivariate normal distribution defined by the mean
+  positions of an equally spaced column of points. We gave the distribution at
+  each point along the column the same standard deviation, $\sigma_z$, shown  in
+  by Table~\ref{table:quenched_disorder}. We defined a covariance matrix such
+  that the covariance, $v$, of the distance, $d$, between scatterers decays
+  exponentially from $v$ according to the equation $ve^{-z/L}$, where $L$ is the
+  correlation length. Experimentally, the correlation length can be estimated as
+  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$. Accordingly,
+  the correlation length of the experimental system is $\geq$ 9 $\AA$. The value
+  may be larger since the peak is likely broadened. We simulated the structure
+  factor of a simple system built as described above with a correlation length of
+  30 $\AA$. We chose 30 $\AA$ in order to exaggerate the effect of correlation
+  length for visual purposes. Subsequent structure factor calculations are all
+  done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section
+  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$
+  cross-section (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in
+  experiment. Additionally, there is a near 20 \% increase in the maximum
+  intensity of R-$\pi$ when the distances between scatterers are correlated.
 
@@
 
-  The correlation length of vertically stacked scatterers in our simulations are
-  in reasonable agreement with experiment. Since it is not feasible for us to simulate
-  membranes with much taller columns for increased $q_z$ resolution, and because the 
-  peak shape is convoluted by the extremely intense maximum of R-$\pi$, we measured 
-  correlation length by plotting the one-dimensional pair distribution function, $g(z)$,
-  for the centers of mass of monomer phenyl rings (Figure~\ref{fig:correlation}). 
+  The correlation length of vertically stacked scatterers in our simulations
+  are in reasonable agreement with experiment. Since it is not feasible for us to
+  simulate membranes with much taller columns for increased $q_z$ resolution, and
+  because the peak shape is convoluted by the extremely intense maximum of
+  R-$\pi$, we measured correlation length by plotting the one-dimensional pair
+  distribution function, $g(z)$, for the centers of mass of monomer phenyl rings
+  (Figure~\ref{fig:correlation}). 
   %We used this 
@@
   \end{subfigure}  
-  \caption{1D correlation functions of the center of masses of aromatic head groups, $g(z)$, show
-  decaying oscillatory behavior. We calculated the correlation length by fitting a decaying exponential
-  function (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The correlation length is
-  longer for ordered basin systems (Table~\ref{table:correlation_length}).
-  We did not attempt to calculate the correlation length for (d) because there are no clear peaks. We 
-  assume that its correlation is less than the vertical distance between monomers.}\label{fig:correlation}
+  \caption{1D correlation functions of the center of masses of aromatic head
+	  groups, $g(z)$, show decaying oscillatory behavior. We calculated the
+	  correlation length by fitting a decaying exponential function
+	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
+	  correlation length is longer for ordered basin systems
+	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
+	  correlation length for (d) because there are no clear peaks. We assume that its
+	  correlation is less than the vertical distance between monomers.}\label{fig:correlation}
   \end{figure}
@@
 
-  %BJC8: The next couple paragraphs is all old stuff that can likely be cut down a bit. But I think 
-  % this is where I'd put this discussion.
-  Monomers in the ordered basin stack closer together than those in the disordered basin
-  (Table~\ref{table:correlation_length}). We calculated the equilibrated vertical distance,
-  $\mathit{d}_{equil}$, between monomers using Equation~\ref{eqn:decaying_sinusoid}. 
-  Monomers in the ordered basin stack ca. 0.2 and 0.3 \AA~closer than those built in the 
-  disordered basin in the sandwiched and parallel displaced configurations respectively. 
-  The distance between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all 
-  cases, with disordered basins at the high part of that range, 0.2 and 0.3 \AA~more distant.
-  %MRS9: GAFF could OVER predict pi-pi stacking, best to include citations here that it does indeed overpredict.
-  %BJC9: Turns out the Jankowski group was using oplsaa, not GAFF (they said GAFF to me). Will search for other
-  % references.
-  This behavior is not surprising since GAFF models atoms as point charges and does not 
-  appropriately model the aromatic $\pi-\pi$ interactions which would make it more energetically
-  favorable for the monomers to stack closer together. Additionally, it is possible that the 
-  tails prevent close stacking of monomer head groups and we do not achieve the timescales 
-  necessary for them to rearrange into a necessarily more tightly packed configuration. Since 
-  ordered basin systems pack closest together, they are likely the best choice for transport 
-  studies.
+  Monomers in the ordered basin stack closer together than those in the
+  disordered basin (Table~\ref{table:correlation_length}). We calculated the
+  equilibrated vertical distance, $\mathit{d}_{equil}$, between monomers using
+  Equation~\ref{eqn:decaying_sinusoid}. Monomers in the ordered basin stack ca.
+  0.2 and 0.3 \AA~closer than those built in the disordered basin in the
+  sandwiched and parallel displaced configurations respectively. The distance
+  between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all
+  cases, with disordered basins at the high part of that range, 0.2 and 0.3
+  \AA~more distant.
+  % MRS9: GAFF could OVER predict pi-pi stacking, best to include citations here
+  % that it does indeed overpredict.  % BJC9: Turns out the Jankowski group was using oplsaa, not GAFF (they said
+  % GAFF to me). Will search for other references.
+  This behavior is not surprising since GAFF models atoms as point charges and
+  does not appropriately model the aromatic $\pi-\pi$ interactions which would
+  make it more energetically favorable for the monomers to stack closer together.
+  Additionally, it is possible that the tails prevent close stacking of monomer
+  head groups and we do not achieve the timescales necessary for them to
+  rearrange into a necessarily more tightly packed configuration. We equilibrated
+  the system at 500K in an attempt to coerce the tails into a more tightly packed
+  configuration, however we saw no improvement over our 300K models. See section
+  S-TBD for details. Overall, head groups in the ordered basin systems pack 
+  closest together and are likely the best choice for transport studies.
 
@@
   The correlation length of the parallel displaced, ordered basin system shows
-  the closest agreement with experiment (Table~\ref{table:correlation_length}). We calculated the 
-  correlation length of each system using Equation~\ref{eqn:decaying_exponential}. We could
-  not extract a reliable correlation length from the disordered parallel displaced configuration
-  since the peaks do not show clear patterns that can easily be fit to an exponential decay. The 
-  correlation length of both sandwiched systems is relatively low because the height of the first
-  peak of $g(z)$ is so high. The peak height indicates the degree of local ordering and influences
-  the intensity of R-$\pi$. If vertically adjacent sandwiched head groups were less ordered, which
-  might be achieved with much longer simulations, then the leading peak intensity should decrease and
-  the correlation length would increase. We expect that the leading peak would only get more intense 
-  if monomers stacked 3.7 \AA~apart. Conversely, parallel displaced head groups are not as confined
-  by their vertically adjacent neighbors. This z-direction translational freedom may still be 
-  feasible if monomers stack 3.7 \AA~apart in a parallel displaced configuration, meaning the system
-  would maintain a correlation length and R-$\pi$ intensity in relative agreement with experiment.
-
-  Increased thermal noise in the $z$-direction causes a drop in the intensity of R-$\pi$, however 
-  the $q_r$ profile remains unchanged. When we increase the thermal noise in the $z$-direction by
-  12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of R-$\pi$ respectively (Figure
-  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections have the same shape
-  (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp Bragg-like peaks are not consistent with 
-  experiment.
-
-  % BJC9: Might be worth acknowledging:
-  % The peaks are spaced apart according to the pore spacing, and line up with R-alkanes.
-
-%  \begin{figure}[!htb]
-%  \centering
-%  \begin{subfigure}{0.3\textwidth}
-%  \includegraphics[width=\textwidth]{sf_qy_correlation_L10.png}  %BJC9: z_variance = 2.074 angstroms
-%  \caption{}\label{fig:sf_znoise_control}
-%  \end{subfigure}
-%  \begin{subfigure}{0.3\textwidth}
-%  \includegraphics[width=\textwidth]{sf_qy_3xdecrease.png}  %BJC9: z_variance = 2.65 angstroms
-%  \caption{}\label{fig:3xdecrease}
-%  \end{subfigure}
-%  \begin{subfigure}{0.3\textwidth}
-%  \includegraphics[width=\textwidth]{sf_qy_15xdecrease.png}  %BJC9: z_variance = 3.4 angstroms
-%  \caption{}\label{fig:15xdecrease}
-%  \end{subfigure}
-%  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
-%  however the $q_r$ cross-section profile does not change. (a) The maximum intensity of R-$\pi$ is ca. 20 
-%  when we use the same level of noise present in the atomistic simulation. (b) The intensity of R-$\pi$ 
-%  decreases by a factor of 3, relative to the background intensity, if we increase thermal noise by 11\% 
-%  in the $z$-direction. (c) The intensity of R-$\pi$ decreases by a factor of 15, relative to the background
-%  intensity, when we increase thermal noise by 28\% in the $z$-direction.}\label{fig:znoise}
-%  \end{figure}
+  the closest agreement with experiment (Table~\ref{table:correlation_length}).
+  We calculated the correlation length of each system using
+  Equation~\ref{eqn:decaying_exponential}. We could not extract a reliable
+  correlation length from the disordered parallel displaced configuration since
+  the peaks do not show clear patterns that can easily be fit to an exponential
+  decay. The correlation length of both sandwiched systems is relatively low
+  because the height of the first peak of $g(z)$ is so high.
+
+% BJC9: omitted because these are not strong points
+%  The peak height
+%  indicates the degree of local ordering and influences the intensity of R-$\pi$.
+%  If vertically adjacent sandwiched head groups were less ordered, which might be
+%  achieved with much longer simulations, then the leading peak intensity should
+%  decrease and the correlation length would increase. We expect that the leading
+%  peak would only get more intense if monomers stacked 3.7 \AA~apart. Conversely,
+%  parallel displaced head groups are not as confined by their vertically adjacent
+%  neighbors. This z-direction translational freedom may still be feasible if
+%  monomers stack 3.7 \AA~apart in a parallel displaced configuration, meaning the
+%  system would maintain a correlation length and R-$\pi$ intensity in relative
+%  agreement with experiment.
+
+  Increased thermal noise in the $z$-direction causes a drop in the intensity
+  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
+  thermal noise in the $z$-direction by 12\% and 27\%, we see a 3 and 15-fold
+  decrease in the maximum intensity of R-$\pi$ respectively (Figure
+  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections
+  have the same shape (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp
+  Bragg-like peaks are not consistent with experiment.
 
@@
   \end{subfigure}
-  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
-  however the $q_r$ cross-section profile does not change. (a) The intensity of R-$\pi$ drops precipitously
-  as we increase $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the background intensity
-  as seen in our simulation (blue) by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase 
-  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$ decreases with increasing $\sigma_z$,
-  the peak shape remains the same.}\label{fig:znoise}
+  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
+  thermal noise in the z-direction, however the $q_r$ cross-section profile does
+  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
+  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
+  background intensity, as seen in our simulation (blue) by a factor of 3 when we
+  increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
+  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$
+  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
   \end{figure}
 
-  When we allow monomer columns to move independently in the z-direction, the intensity
-  of R-$\pi$ drops and the $q_r$ cross-section of the simulated diffraction patterns 
-  smooths out. We created simple systems with varying amounts of association between columns. 
-  In the low limit, the center of mass of columns are situated at the same $z$-coordinate. 
-  This is how all simple systems have been created up to this point. We allow increasing 
-  independence of columns by randomly shifting each column in the $z$-direction using a uniform
-  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We
-  limit this discussion to the sandwiched configuration since it is not
-  feasible for columns in the parallel displaced configuration, as we have set them up, to move
-  past each other. The trends seen above apply to both the sandwiched and parallel displaced systems.
-  Allowing columns to move independently smooths out the $q_r$ cross-section
-  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp peaks. The
-  intensity of R-$\pi$ decreases with increasing column independence. We see an 8-fold decrease
-  in the intensity of R-$\pi$ when $f=1$ versus when $f=0$.
+  When we allow monomer columns to move independently in the $z$-direction, the
+  intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
+  diffraction patterns smooths out. We created simple systems with varying
+  amounts of association between columns. In the low limit, the center of mass
+  of columns are situated at the same $z$-coordinate. This is how all simple
+  systems have been created up to this point. We allow increasing independence of
+  columns by randomly shifting each column in the $z$-direction using a uniform
+  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges
+  between 0 and 1. We limit this discussion to the sandwiched configuration since
+  it is not feasible for columns in the parallel displaced configuration, as we
+  have set them up, to move past each other. The trends seen above apply to both
+  the sandwiched and parallel displaced systems. Allowing columns to move
+  independently smooths out the $q_r$ cross-section
+  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in
+  sharp peaks. The intensity of R-$\pi$ decreases with increasing column
+  independence. We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$
+  versus when $f=0$. It is likely that the discrepancy between the intensity of 
+  R-$\pi$ generated from our simulations versus experiment is due
+  to highly correlated columns in our initial configurations.
 
@@
   \end{subfigure}
-  \caption{As we increase column independence using the $f$ parameter, the intensity of R-$\pi$
-  decreases and the $q_r$ cross-section of the simulated diffraction pattern becomes more smooth.
-  (a) When we place all columns at the same z coordinate, $f$ = 0, the intensity of R-$\pi$ is
-  18.3 and is characterized by sharp Bragg-like peaks. (b) When columns have a moderate amount of
-  independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold to 3.7. The edges of the
-  peak are beginning to smooth out, but sharp peaks still exist. (c) When columns are completely
-  independent, $f$ = 1, the intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
+  \caption{As we increase column independence using the $f$ parameter, the
+	  intensity of R-$\pi$ decreases and the $q_r$ cross-section of the simulated
+	  diffraction pattern becomes more smooth.  (a) When we place all columns at the
+	  same reference $z$ coordinate, $f$ = 0, the intensity of R-$\pi$ is 18.3 and is
+	  characterized by sharp Bragg-like peaks. (b) When columns have a moderate
+	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
+	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
+	  still exist. (c) When columns are completely independent, $f$ = 1, the
+	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
           relatively smooth.}\label{fig:column_displacement}
@@
 
-  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$ cross-section of 
-  R-$\pi$ to decrease. We modified the disorder in both the $r$ and $\theta$ directions by
-  multiplying their values by a factor of 0.5 and 2 (Figure~\ref{fig:qy_fwhm}). When we cut
-  the noise in half, the FWHM increases by 88 \%. When we double the noise, the FWHM 
-  decreases by 51 \%.
+  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
+  cross-section of R-$\pi$ to decrease. Using a system with uncorrelated columns,
+  we modified the disorder in both the $r$ and $\theta$ directions by multiplying
+  their values by a factor of 0.5 and 2 (Figure~\ref{fig:qy_fwhm}). When we cut
+  the noise in half, the FWHM increases by 88 \%. When we double the noise, the
+  FWHM decreases by 51 \%.
 
@@
   \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
-  \caption{Increasing the amount of disorder in the $xy$ plane decreases the FWHM of the 
-  $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and $theta$ disorder in
-  half (Noise factor = 0.5), the FWHM increases by 88\%. When we double the disorder 
-  (Noise factor = 2), the FWHM decreases by 51\%.}\label{fig:qy_fwhm}
+  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
+	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
+	  $theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
+	  we double the disorder (Noise factor = 2), the FWHM decreases by
+	  51\%.}\label{fig:qy_fwhm}
   \end{figure}
 
-  We can use what we learned above in order to construct a better model, however there
-  will still be shortcomings. We can decrease the intensity of R-$\pi$ if we incorporate
-  more $z$-directional noise, which may come from increasing the system's temperature.
+  We can use what we learned above in order to construct a better model,
+  however there will still be shortcomings. We can decrease the intensity of
+  R-$\pi$ if we incorporate more $z$-directional noise, which may come from
+  increasing the system's temperature. 
   % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
   % temperature? Is decreasing the force constant between bonds viable? 
-  We can adjust the parameters for aromatic carbons so that head groups stack more 
-  closely together. Perhaps the simplest thing to do is to create initial configurations
-  whose columns are displaced randomly in the $z$-direction in order to mimic independence.
-  Ultimately, we will need extremely long simulation times so that monomers within 
-  columns can rearrange and sample enough independent configurations to generate a robust
-  simulated XRD pattern.
-
-  The architecture of each column is likely somewhere between sandwiched and parallel 
-  displaced. The parallel displaced configuration that we have simulated in this paper
-  is an exaggerated manifestation of the parallel displaced $\pi-\pi$ stacking mode. 
-  The simulated XRD pattern shows faint off-axis features at the same $q_r$ value as
-  R-double which is only in patterns generated from parallel displaced configurations. 
-  The monomers may prefer to be parallel displaced, but their displacement is likely 
-  only slightly shifted, on the $xy$ plane, from the center of mass of their vertically
-  adjacent neighbors. In this way, columns can more easily act independently while 
-  maintaining a parallel displaced structure.
-
-%  \item Stacked disks (layers)
-%	  \item No influence on intensity
-%	  \item Some influnce on FWHM (?)
-
-%  There is not a single reason we can clearly identify for the high intensity of R-$\pi$ in our simulations.
-%  We used one-dimensional pair distribution functions of the centers of masses of monomer
-%  phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
-%  columns and the degree to which they are correlated. These metrics helped us dissect the 
-%  various contributions to R-$\pi$. Figure~\ref{fig:correlation} shows $g(z)$ for all 
-%  systems tested.
-
-%  The first peak of $g(z)$ is larger in the ordered
-%  basin systems compared to those in the disordered basin. This observation is indicative
-%  of a higher degree of local ordering in the ordered basin systems which causes an
-%  increase in the intensity of R-$\pi$.
-
-  %MRS7: not a strong thesis sentence.
-
-  %The amount of noise in the correlation function and the lack of an initial peak suggests that 
-  %the correlation length is less than $\mathit{d}_{equil}$.
-  %BJC6: not supported by data vv
-%  In general, we see that correlation length increases as monomers stack closer together. The same
-%  trend has been seen in molecular dynamics studies of polymer fluids~\cite{koshy_density_2003}.
-%  We hypothesize that the correlation length of the sandwiched configuration would increase to a
-%  value near experiment if monomers packed closer together.
-
-%  The persistent oscillatory behavior of the correlation function may in part explain the high
-%  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
-%  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
-%  simulated systems, especially the sandwiched configurations, shows peaks which persist across
-%  the entire correlation function. If the peaks, at large values of z, instead decay to 1 uniformly,
-%  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
-%  The monomer head groups in our simulations do not move enough on the timescales simulated to 
-%  create the noise which would cause such behavior. See Section S-\ref{S-section:rpi_ft} of the
-%  supporting information for illustrative examples.
-
-  The system size in the $z$-direction does not significantly alter the intensity of R-$\pi$. We equilibrated a 
-  sandwiched system with twice as many monomers per column so that the system size doubled in 
-  the z-direction. The correlation length increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA, 
-  and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the correlation functions
-  are nearly identical (See Figure~S-\ref{S-fig:z_correlation_overlay}).
-
-  %MRS7: question - pushing Matt on this, he seemed to imply that the high value of the peaks indicated large
-  %LOCAL ordering, and that defects/misaligned pores would give rise to BROADENING, but wouldn't change the 
-  %intensity of the peaks that much.  If so, this isn't a great explanation. 
-  %BJC6: worked this into other paragraphs. I find this paragraph awkward and the figure unnecessary.
-%  The simulated intensity of R-$\pi$ is also more intense than experiment due to strong local
-%  ordering. Nearly all of the intensity in R-$\pi$ of our simulated patterns is concentrated 
-%  at a single point. Figure~\ref{fig:simulated_adjusted_colorbar} shows the simulated pattern
-%  of the ordered sandwiched configuration with the upper boundary on the colorbar adjusted to
-%  be 6x higher than those shown in Figure~\ref{fig:XRDsim}. The only distinguishable reflections
-%  are those of R-$\pi$ and R-pores. In the experimental pattern 
-%  (Figure~\ref{fig:experimental_adjusted_colorbar}), the intensity is more evenly spread out
-%  over all of R-$\pi$. 
-  % BJC5: I'm not sure how well supported the above paragraph is by the below figure. Need to figure 
-  % out what to do about it
-  % BJC5: Could it also be related to noise in xy direction?
-  % BJC5 : I think my original intent was to explain it as tortuosity. But it's not clear if the
-  % reflection is arced
+  We can also decrease the intensity of R-$\pi$, in addition to smoothing the
+  $q_y$ cross-section by creating initial configurations whose columns are
+  displaced randomly in the $z$-direction. We can achieve better averages if we
+  create systems with more pores in the unit cell. In order to make head groups
+  stack closer together, we can adjust the parameters for aromatic carbons so
+  that head groups stack more closely together. Ultimately, we will need
+  extremely long simulation times so that monomers within columns can rearrange
+  and sample enough independent configurations to generate a robust simulated XRD
+  pattern.
+
+  The architecture of each column is likely in between sandwiched and parallel
+  displaced. The parallel displaced configuration that we have simulated in this
+  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
+  stacking mode. The simulated XRD pattern shows faint off-axis features at the
+  same $q_r$ value as R-double which is only present in patterns generated from
+  parallel displaced configurations. The same feature is present in the
+  experimental pattern. The monomers may prefer to be parallel displaced, but
+  their displacement is likely only slightly shifted, on the $xy$ plane, from the
+  center of mass of their vertically adjacent neighbors. In this way, columns can
+  more easily act independently while maintaining a parallel displaced structure.
+
+  % BJC9: Does it still make sense to have this in here? I think we thought that
+  % making the system taller might result in a more disordered structure, leading
+  % to weaker distance correlations between stacked monomers and a reduced R-pi. 
+  % But I've shown that the intensity of R-pi is only weakly dependent on correlation
+  % length (20 % difference between correlation length of 0 and 30) and even if there
+  % is additional xy noise (for some reason), it will not not decrease R-pi max 
+  % intensity. Also, we are getting near the right correlation length (from g(z)
+  % and kind of from XRD), which is less than the length of the box. I could
+  % just move this to supplemental.   
+  The system size in the $z$-direction does not significantly alter the
+  intensity of R-$\pi$. We equilibrated a sandwiched system with twice as many
+  monomers per column so that the system size doubled in the z-direction. The
+  correlation length increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA,
+  and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the
+  correlation functions are nearly identical (See
+  Figure~S-\ref{S-fig:z_correlation_overlay}).
 
@@
 
-% BJC5: this is no longer a section after reorganization
-%  \subsubsection{Layer partitioning}
-%
-%  In our simulations, layers are well-defined and persistent, answering question
-%  (\ref{point:layers}). We established our conclusion by plotting the two
-%  dimensional pair distribution function, $g(y,z)$ of head group phenyl rings
-%  using Equation~\ref{eqn:correlation} (Figure \ref{fig:yz_correlation}). In both
-%  configurations, the phenyl rings stack in the z-direction, along $y=0$, and
-%  clear layers are formed. The layers in the sandwiched configuration are more
-%  defined than those in the parallel displaced configuration and are strongly
-%  correlated with adjacent layers. We also observe correlation of layers between
-%  pores indicated by the non uniformity in $g(y,z)$ in adjacent columns (along $y
-%  = \pm 3.65$). Parallel displaced layers display weaker correlations but do not
-%  decay in their intensity as z increases. We do not see correlation between
-%%MRS6: correlations of what between pores?
-%  pores, however correlations within pores are strong throughout the length of
-%  the unit cell since there is no noticeable decay in layer intensity. 
-%
 %  \begin{figure}
@@
 
-%  \subsubsection{Initial Layer Spacing Affects System Equilibration}
-%
-%  All systems up to this point were built with layers stacked 3.7 \AA~apart.
-%  When we build systems with layers stacked 5.0 \AA~apart and then let them
-%  equilibrate, we observe long-term stability of a qualitatively different
-%  configuration, suggesting that we have found another metastable free energy
-%  basin, further corroborating question (\ref{point:metastable}). 
-%  %The basins are
-%  %differentiated by their relative degrees of ordering resulting from different
-%  %spatial arrangements. 
-%  For reasons we will develop in the next segment of our
-%  discussion, configurations initially built with layers stacked 5.0 \AA~apart 
-%  will be grouped into the disordered pore basin, while those built with layers
-%  initially stacked 3.7 \AA~apart will be grouped into the ordered pore basin.
-%
-%  The equilibrated pore spacing and distance between layers are different in
-%  the disordered pore basin. For both head group stacking arrangements, we
-%  observe an increase in the equilibrated distance between layers
-%  (Fig.~\ref{fig:dbwl_disordered}) and a corresponding decrease in pore spacing
-%  (Fig.~\ref{fig:p2p_disordered}).
-%
-%  The simulated X-ray diffraction patterns indicate further structural
-%  differences. In the parallel displaced configuration, almost all contrast
-%  between R-spots and R-alkanes fades (Figure~\ref{fig:offset_disordered_xrd}).
-%  In the sandwiched configuration, R-spots is present, but there are only two
-%  spots located at the intersection of $q_z=0$ with R-alkanes.
-%  (Figure~\ref{fig:layered_disordered_xrd}). 
-%
-%% BJC: in the interest of being concise, I leave this out for now.
-%%  The sandwiched and parallel displaced assemblies do not deviate from their
-%%  initial head group arrangement. R-double is still faintly visible in the
-%%  parallel displaced configuration and is absent in the sandwiched simulated
-%%  diffraction pattern. The spectroscopic signatures are unique to the two
-%%  different head group configurations.
-%
-%  \begin{figure}[!hbt]
-%        \centering
-%        \begin{subfigure}{0.45\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth]{dbwl.png}
-%                \caption{}~\label{fig:dbwl_disordered}
-%        \end{subfigure}%
-%        \begin{subfigure}{0.45\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth]{p2p2.png}
-%                \caption{}~\label{fig:p2p_disordered}
-%        \end{subfigure}
-%        \begin{subfigure}{0.45\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth]{disorder_offset_rzplot.png}
-%                \caption{}~\label{fig:offset_disordered_xrd}
-%        \end{subfigure}%
-%        \begin{subfigure}{0.45\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth]{disorder_rzplot.png}
-%                \caption{}~\label{fig:layered_disordered_xrd}
-%        \end{subfigure}
-%	\caption{There are distinct differences between the disordered and ordered pore systems. 
-%		When layers are initially stacked 5\AA~ apart, the distance
-%		between layers increases (a) and the pore spacing decreases (b) in comparison to
-%		the ordered pore systems. The simulated
-%		XRD patterns of disordered pore systems are also appreciably different, most 
-%		notably in the region bounded by R-alkanes. The disordered pore
-%		systems started in the parallel displaced configuration (c) does not show R-spots
-%		or R-$\pi$ which suggests that head groups are not associating with each other
-%		and tails are distributed nearly isotropically. The disordered pore system
-%		started in the sandwiched configuration (d) does not show R-$\pi$ but R-spots 
-%		is present in different locations because the tails are packed in a different
-%		motif.}
-%  \end{figure}
-%
-%  %BJC: this may belong in methods, but I think it might fit here because it
-%  % gives context for the choice of functional form to fit
-%
-%  We quantified order in the z-direction by measuring the correlation lengths
-%  of all configurations. We measured the correlation length, L, by fitting $g(z)$
-%  using a non-linear least squares algorithm subject to a function of the form:
-%  \begin{equation}
-%  	1 + Asin(Bx + C)e^{-z/L}
-%        \label{eqn:correlation_fit}
-%  \end{equation}
-%  where z is the independent variable and all other variables are fitting
-%  parameters. The correlation length for each system is given in
-%  Table~\ref{table:nematic}.
-%
-%  Correlation lengths are shorter in the disordered pore basin than in the
-%  ordered pore basin. Layers in the ordered pore basin are strongly correlated
-%  with neighboring layers up to more than 10 layers away. This behavior deviatbecomes smalleres
-%  from experimental evidence. The experimental correlation length (See
-%  Supporting Information for details its derivation) suggests that layers are
-%  correlated with about 3 neighboring layers which is closer to the values
-%  exhibited by the disordered pore basin. We may need to simulate a system with
-%  many more layers in order to reduce the correlation contributed by periodic
-%  copies of the system. 
-%
-%%MRS6: not sure if we WANT to do this, but could do a simulation with 2x as many layers and see if the correlation changes.
-%%BJC2: have one that is 3x going right now
-%
-%  We calculated the nematic order parameter for each system using Equation
-%  \ref{eqn:nematic_order_parameter}. The calculated values of S are presented in
-%  Table \ref{table:nematic}. The full distributions of angles between director
-%  \textbf{n} and vectors orthogonal to monomer phenyl rings are presented in the
-%  Supporting Information. In general, ordered pore basin systems are more
-%  nematically ordered than disordered pore basin systems and sandwiched
-%  configuration systems are more nematically ordered than parallel displaced
-%  configuration systems. The head groups of the disordered pore basin have more
-%  rotational freedom about the xy plane likely due to the larger separation
-%  between layers. Similarly, monomers situated in the sandwiched configuration
-%  are constrained by other monomers stacked directly above and below them, while
-%  monomers in the parallel displaced configuration have no direct neighbors
-%  vertically which provides them with more rotational freedom. 
-%
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{ccc}
-%  \toprule
-%  System & Correlation Length (\AA) & Nematic Order Parameter (S) \\
-%  \midrule
-%  Sandwiched, Ordered & 41 $\pm$ 3 & 0.659 $\pm$ 0.003 \\
-%  Parallel Displaced, Ordered & 86 $\pm$ 14 & 0.601 $\pm$ 0.003 \\
-%  Sandwiched, Disordered & 17 $\pm$ 3 & 0.565 $\pm$ 0.002 \\
-%  Parallel Displaced, Disordered & 9 $\pm$ 1 & 0.503 $\pm$ 0.002 \\
-%  Experiment & 10 $\pm$ 1 & -- \\
-%  \bottomrule
-%  \end{tabular}
-%  \caption{The nematic order parameter, S, is higher when layers are initially spaced
-%  3.7 \AA apart. In general, the sandwiched configuration has higher nematic order
-%  than the parallel displaced configuration. Correlation lengths are higher in
-%  the ordered pore basin. Correlation lengths in the disordered pore basin are
-%  in closer agreement with experiment. WHY IS THIS BOLD??!}~\label{table:nematic}
-%%MRS6: for some reason, might be set in the jpcbfk package?
-%  \end{table}
-
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{ccc}
-%  \toprule
-%  System & Layer Separation & Correlation Length \\
-%  \midrule
-%  Sandwiched & 4.39 \AA & 41 $\pm$ 3 \AA \\
-%  Parallel Displaced & 4.38 \AA & 86 $\pm$ 14 \AA \\
-%  Experiment* & 3.7 \AA & 10 $\pm$ 1 \AA \\  
-%  \bottomrule
-%  \end{tabular}
-%  \caption{Uncertainties are derived from the diagonal entries in the
-%	  covariance matrix calculated from a non-linear least squares fit to the data.
-%	  *See supplemental information for derivation of experimental correlation
-%	  length}~\label{table:correlation_length}
-%  \end{table}
-
-%  %BJC: this might be better situated before the numerical calculations that go 
-%  %into Table 1
-%  We observe evidence of disorder in the xy plane of the disordered pore basin when
-%  we plot the two dimensional pair distribution function, $g(x,y)$, between the
-%  centers of mass of monomer phenyl rings (Figure \ref{fig:xy_correlation}). The
-%  difference is most apparent in the plots of the sandwiched configurations. In
-%  the ordered pore basin, head groups primarily stay stacked on top of each other
-%  while in the disordered pore basin, head groups exhibit more motion about the pore
-%  center and even drift into the middle of the pore. $g(x,y)$ for the parallel displaced
-%  configuration is less informative since adjacent layers are displaced in a way that
-%  occupies the gaps that are seen in $g(x,y)$ for the sandwiched configuration 
-%
-%  \begin{figure}
-%  \begin{subfigure}{1\linewidth}
-%        \centering
-%        \begin{subfigure}{0.47\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth]{layered_xy_correlation.png}
-%                \caption{Sandwiched, Ordered Pore Basin}~\label{fig:sandwich_xy}
-%        \end{subfigure}
-%        \begin{subfigure}{0.47\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth]{disorder_xy_correlation.png}
-%                \caption{Sandwiched, Disordered Pore Basin}~\label{fig:disorder_sandwich_xy_correlation}
-%       \end{subfigure}
-%       \begin{subfigure}{0.47\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth]{offset_xy_correlation.png}
-%                \caption{Parallel Displaced, Ordered Pore Basin}~\label{fig:offset_xy}
-%        \end{subfigure}
-%        \begin{subfigure}{0.47\linewidth}
-%                \centering
-%                \includegraphics[width=\linewidth]{disorder_offset_xy_correlation.png}
-%                \caption{Parallel Displaced, Disordered Pore Basin}~\label{fig:disorder_offset_xy_correlation}
-%        \end{subfigure}
-%  \end{subfigure}
-%  \caption{$g(x,y)$ for sandwiched and parallel displaced configurations in the
-%	  ordered and disordered pore basins illustrates the increase in xy plane
-%	  disorder when initial configuration layer stacking distance is increase from
-%	  3.7 \AA~to 5 \AA~apart.}\label{fig:xy_correlation}
-%  \end{figure}
-
   \subsubsection{Origin of R-double}\label{section:rdouble}
@@
   the position of monomers in parallel displaced configurations alternate every other layer, 
-  we know that such a helical configuration will not produce R-double, but only off-axis 
+  we know that such a screw axis type configuration will not produce R-double, but only off-axis 
   reflections at the same $q_z$ value~\cite{harburn_atlas_1975}. There is not a unique solution

### 2018-08-08 Ben_Manuscripts/structure_paper/Draft.tex
Draft updates

@@
 
-  \subsubsection{Origin of R-spots}\label{section:rspots}
+  \subsubsection{The origin of R-spots}\label{section:rspots}
 
@@
   our membrane system, simulated at 300K, does not fully represent the true structure at 300K.
-  Lowering the temperature to 280K helped us to better resolve R-spots. 
+  Lowering the temperature to 280K helped us to better resolve R-spots (Figure~\ref{fig:sandwiched280K}). 
 %  The relative intensity 
@@
 
-  R-spots originates from the monomer tails.
   %To understand the most likely origin of R-spots, we determined which atoms
   %gave rise to the feature. 
-  By removing all non-tail atoms from the trajectory
-  and simulating a diffraction pattern with the remaining atoms, we were able to
-  isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
-
-  The tails pack together hexagonally. Since the tails stay nearly flat, we plotted
-  their centroids (Figure \ref{fig:centroids}) and measured the angle between
-  each centroid and its nearest neighbors with respect to the plane of the
-  membrane. We see distinct peaks in the distribution of these angles which are
-  consistent with a hexagonally packed configuration
-  (Figure~\ref{fig:tail_packing}).
+  R-spots originates from the monomer tails. By removing all non-tail atoms from 
+  the trajectory and simulating a diffraction pattern with the remaining atoms, 
+  we were able to isolate the cause of the spots to the tails 
+  (Figure~\ref{fig:tails_rzplot}).
+
+  The tails pack together hexagonally. We plotted the center of mass of the 
+  first four tail atoms of each tail originating from each head group 
+  (Figure \ref{fig:centroids}). We measured the angle between each center of
+  mass and its nearest neighbors with respect to the $xy$ plane of the membrane. 
+  We see distinct peaks in the distribution of these angles located ca. 
+  $-60\degree$, $0\degree$, and $60\degree$ which is consistent with a 
+  hexagonally packed configuration (Figure~\ref{fig:layered_tails}). This 
+  ordering dies off at the tail ends, where there is more space to fill 
+  causing them to pack nearly isotropically (See supporting information).
 
   The peaks in the nearest neighbor angle distribution are consistent with the
-  location of R-spots. The peaks of interest in Figure \ref{fig:layered_tails}
-  are located at $\pm 33 \degree$ which is the same location where the highest
-  intensity of spots are located in the simulated patterns. We confirmed this 
-  by radially integrating the 2D WAXS pattern for 
-  $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
-  and 4.5 \AA~in real space). We observe distinct peaks ca. $30
-  \degree$, in close agreement with the previously measured angle distribution
-  (Figure~\ref{fig:layered_integration}). We performed the same integration on
-  the raw experimental data and found the angle at which R-spots reaches its
-  highest intensity to be $\pm 37 \degree$ which is a reconcilable difference
-  with our simulated results.
+  location of R-spots. The 2D Fourier transform of a simple hexagonal array 
+  constructed based on the peak angles in Figure~\ref{fig:layered_tails}
+  shows reflections in the same locations as R-spots, in addition to vertical 
+  stacking reflections along the $q_z$ axis that would intersect with R-$\pi$
+  (Figure~\ref{fig:hexagonal_ft}).
 
@@
     \centering
-	\includegraphics[width=\textwidth]{centroids_box.png}
+	\includegraphics[scale=0.2]{centroids.png}
   \caption{}\label{fig:centroids}
@@
         	\centering
-	        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
-	        \caption{}~\label{fig:layered_integration}
+	        \includegraphics[width=\linewidth]{hexagonal_ft.png}  % generated from hexagonal_packing.py
+	        \caption{}~\label{fig:hexagonal_ft}
   \end{subfigure}
@@
       simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
-      Since the tails stay relatively flat, we plotted the centroid of each tail 
-      and observed that they pack hexagonally (for example, green colored centroids
-      in the plot surround the red centroid in hexagonal fashion). (e) We hypothesize
+      Since the tails stay relatively flat, we plotted the center of mass of the first
+      four carbon atoms of each tail originating from the head groups (for example,
+      green colored centroids in the plot surround the red centroid in hexagonal fashion).
+      Visually, the packing looks hexagonal. (e) We hypothesize
       that R-spots is the result of ordered tail packing. Defining
-      the membrane plane to be 0\degree, we measured the angles between each alkane 
-      chain tail centroid and its nearest neighbor centroids for the equilibrated 
-      sandwiched configuration simulated at 280K. Peaks that appear in each distribution
-      are centered near $\pm~33\degree$. (f) We radially integrated the simulated XRD
-      patterns of the parallel displaced and sandwiched configuration within the region
-      bounding R-alkanes. Peaks appear in the same location as the angle distributions
-      which corroborates our hypothesis.}~\label{fig:tail_packing}
+      the membrane plane to be 0\degree, we measured the angles between each center of 
+      mass and its nearest neighbor center of masses for the equilibrated 
+      sandwiched configuration simulated at 280K. Peaks appear in the distribution at 
+      $-60\degree$, $0\degree$ and $60\degree$. (f) The Fourier transform of a hexagonally
+      packed grid of points defined by the angles in (e) shows intensity at the same
+      locations where we expect to see R-spots, as well as intensity along the $q_z$ axis
+      where R-$\pi$ would appear.}~\label{fig:tail_packing}
   \end{figure}
@@
   \subsubsection{Discrepancies between experimental and simulated R-$\pi$}\label{section:rpi}
-
-  % BJC8: Is it necessary to focus in on the parallel displaced system for this section? At this
-  % point in the story, I haven't shown that it gives rise to R-double. I think the simple systems
-  % are conceptually easier to grasp with sandwiched columns. Sliding parallel displaced columns
-  % is harder to imagine, and probably not really how the columns are stacked. The parallel displacement
-  % is probably less exagerated. 
-  % BJC8: that said, if we go with just focusing on parallel displaced, then I can move the R-double section
-  % up before this one.
-  % MRS9: I think we should start with larger differences rather than smaller, and arguably the greater intensity of R-pi is 
-  % a bigger difference.
-So it's OK ti put R-double after -- (and it could be that sliding sandwiched columns could still give water h-bonding, since they have carboxyl groups that are on average closer together than sandwiched layered ones).
-  %BJC9: keeping above comments for reference
 
@@
   high in the ordered sandwiched configuration (Table~\ref{table:relative_inensities_300K}).
-%BJC9: keeping below comment for reference  
-%MRS9: should be a little more clear why you mean by ``all systems''.
-In some sense the problem is more that the best explanation might be unaligned columns, which is easier with sandwiched, which are 15 times as much.
-So here it would make more sense to focus on both types of columns, so you can explain how unaligned (sliding) columns also have a mechanism for reduction.
-Note that I don't think the columns have to be dynamically sliding (Which would be hard with all the tails entangled) but can be just off-register statically.
-
+
+  % BJC9: This still needs to be worked out. Rest of section should still hold up
   The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
@@
   We have identified a number of potential ways that simulation conditions,
-  forcefield and initial configurations could affect the intensity of R-$\pi$ as
-  well as its FWHM in the $q_z$ and $q_r$ directions. We assessed each using a
+  forcefield and initial configurations could affect the intensity and shape of
+  R-$\pi$. We assessed each using a
   simplified model. Our simplified model represents each monomer head group as a
@@
   important implications for the reproducibility of this work since both initial
-  configurations and velocity randomization at the beginning of equilibration can
+  configurations and initial velocity randomization can
   lead to different quenched configurations. We measured thermal disorder by
@@
   radial position from the pore center and the angular deviation from equally
-  spaced points surrounding the pore center. The values measured for each system
-  and type of disorder are given in Table~\ref{table:quenched_disorder}.
+  spaced points surrounding the pore center. This method for calculating 
+  quenched order inherently includes thermal disorder. The values measured for
+  each system and type of disorder are given in Table~\ref{table:quenched_disorder}.
 
@@
   as our simulations and then create a trajectory to which we add thermal
-  disorder to the initial configuration in order to create each frame.
-  %BJC9 : The following numbers need to be updated: I want to do 40 trajectories with 1000 frames each for both types of trajectories and compare their mean and uncertainty
-  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this
-  way was 16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000
-  initial configurations, the intensity of R-$\pi$ is 16.42, in close agreement
-  with the mean of 40 simulations.  We use the latter method for the remainder of
-  this work since we can extract the trends we need using a single trajectory at
-  a fraction of the computational cost.
+  noise to each subsequent frame. In this scenario, the positions of each scatterer
+  will not change in a way that significantly affects the intensity of R-$\pi$
+  since most of its character is defined by the far more disordered initial configuration.
+  To uncover the expected intensity of R-$\pi$, we would need to average over many
+  such trajectories. To bypass this expensive calculation, we instead calculate the
+  R-$\pi$ intensity from a trajectory consisting of many independent initial 
+  configurations. This simulates the long time scales over which we expect columns
+  to sample many configurational states. %We use the latter method for the remainder of
+%  this section since we can extract the trends we need using a single trajectory at
+%  a fraction of the computational cost.
+
+ %BJC9 : Could show some number like the following
+%  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this (1st way mentioned above)
+%  way was 16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000
+% initial configurations, the intensity of R-$\pi$ is 16.42, in close agreement
+%  with the mean of 40 simulations.
 
   When we simulated the diffraction pattern of a parallel displaced simple
-  system trajectory of 1000 independent configurations, each created using the
-  parameters for thermal and quenched disorder in order to place points, the
+  system trajectory of 1000 independent configurations, the
   $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
@@
   each point along the column the same standard deviation, $\sigma_z$, shown in
-  by Table~\ref{table:quenched_disorder}. We defined a covariance matrix such
+  Table~\ref{table:quenched_disorder}. We defined a covariance matrix such
   that the covariance, $v$, of the distance, $d$, between scatterers decays
-  exponentially from $v$ according to the equation $ve^{-z/L}$, where $L$ is the
+  exponentially from $v$ according to the equation $ve^{-d/L}$, where $L$ is the
   correlation length. Experimentally, the correlation length can be estimated as
@@
 
+  % BJC9: Got rid of references to R-pi intensity in following paragraph because
+  % I can't directly compare R-pi between two simulations starting from different
+  % initial configs w/ different velocity randomizations.
+  The system size, in the $z$-direction, does not significantly alter $g(z)$. 
+  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
+  system may be necessary to fully capture the correlation function. We 
+  equilibrated a sandwiched system with twice as many monomers per column 
+  so that the system size doubled in the $z$-direction. The correlation length 
+  increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. Visually, the
+  correlation functions are nearly identical and oscillatory behavior persists
+  throughout $g(z)$ in both cases (See Figure~S-\ref{S-fig:z_correlation_overlay}).
+
 % BJC9: omitted because these are not strong points
@@
   of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
-  thermal noise in the $z$-direction by 12\% and 27\%, we see a 3 and 15-fold
-  decrease in the maximum intensity of R-$\pi$ respectively (Figure
-  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections
-  have the same shape (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp
-  Bragg-like peaks are not consistent with experiment.
+  thermal noise of our parallel displaced simple system in the $z$-direction by
+  12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of 
+  R-$\pi$ respectively (Figure~\ref{fig:znoise}). Despite the decrease in 
+  intensity, the 3 cross-sections have the same shape 
+  (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp Bragg-like peaks are
+  not consistent with experiment.
 
@@
   \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
-  thermal noise in the z-direction, however the $q_r$ cross-section profile does
+  thermal noise in the $z$-direction, however the $q_r$ cross-section profile does
   not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
@@
   systems have been created up to this point. We allow increasing independence of
-  columns by randomly shifting each column in the $z$-direction using a uniform
+  columns by randomly shifting each column in the $z$-direction according to a uniform
   distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges
@@
   have set them up, to move past each other. The trends seen above apply to both
-  the sandwiched and parallel displaced systems. Allowing columns to move
+  the sandwiched and parallel displaced systems. 
+  %BJC9: ^need to prove that in supplemental?  
+  Allowing columns to move
   independently smooths out the $q_r$ cross-section
@@
   versus when $f=0$. It is likely that the discrepancy between the intensity of 
-  R-$\pi$ generated from our simulations versus experiment is due
+  R-$\pi$ generated from our simulations versus experiment is primarily due
   to highly correlated columns in our initial configurations.
@@
 
+  The architecture of each column is likely in between sandwiched and parallel
+  displaced. The parallel displaced configuration that we have simulated in this
+  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
+  stacking mode. The experimental WAXS pattern shows faint off-axis features at the
+  same $q_r$ value as R-double which is only present in simulated patterns generated from
+  parallel displaced configurations. The monomers may prefer to be parallel displaced, but
+  their displacement is likely only slightly shifted, on the $xy$ plane, from the
+  center of mass of their vertically adjacent neighbors. In this way, columns can
+  more easily act independently while maintaining a parallel displaced structure.
+
   We can use what we learned above in order to construct a better model,
@@
   create systems with more pores in the unit cell. In order to make head groups
-  stack closer together, we can adjust the parameters for aromatic carbons so
-  that head groups stack more closely together. Ultimately, we will need
-  extremely long simulation times so that monomers within columns can rearrange
-  and sample enough independent configurations to generate a robust simulated XRD
-  pattern.
-
-  The architecture of each column is likely in between sandwiched and parallel
-  displaced. The parallel displaced configuration that we have simulated in this
-  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
-  stacking mode. The simulated XRD pattern shows faint off-axis features at the
-  same $q_r$ value as R-double which is only present in patterns generated from
-  parallel displaced configurations. The same feature is present in the
-  experimental pattern. The monomers may prefer to be parallel displaced, but
-  their displacement is likely only slightly shifted, on the $xy$ plane, from the
-  center of mass of their vertically adjacent neighbors. In this way, columns can
-  more easily act independently while maintaining a parallel displaced structure.
-
-  % BJC9: Does it still make sense to have this in here? I think we thought that
-  % making the system taller might result in a more disordered structure, leading
-  % to weaker distance correlations between stacked monomers and a reduced R-pi. 
-  % But I've shown that the intensity of R-pi is only weakly dependent on correlation
-  % length (20 % difference between correlation length of 0 and 30) and even if there
-  % is additional xy noise (for some reason), it will not not decrease R-pi max 
-  % intensity. Also, we are getting near the right correlation length (from g(z)
-  % and kind of from XRD), which is less than the length of the box. I could
-  % just move this to supplemental.   
-  The system size in the $z$-direction does not significantly alter the
-  intensity of R-$\pi$. We equilibrated a sandwiched system with twice as many
-  monomers per column so that the system size doubled in the z-direction. The
-  correlation length increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA,
-  and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the
-  correlation functions are nearly identical (See
-  Figure~S-\ref{S-fig:z_correlation_overlay}).
+  stack closer together, we can adjust the force field parameters for aromatic 
+  carbons. Ultimately, we will need extremely long simulation times, or enhanced
+  sampling techniques so that monomers within columns can rearrange and sample
+  enough independent configurations to generate a robust simulated XRD pattern.
 
@@
 %  higher than all other plots.}\label{fig:intense_rpi}
-%  \end{figure}
-
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%	\centering
-%	\includegraphics[width=\textwidth]{layered_yz_correlation.png}
-%	\caption{}\label{fig:layered_yz_correlation}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%        \centering
-%        \includegraphics[width=\textwidth]{offset_yz_correlation.png}
-%        \caption{}\label{fig:offset_yz_correlation}
-%  \end{subfigure}
-%  %MRS6: have the same color scale in both figures to compare them?
-%  \caption{2D pair distribution functions generated from systems built in the 
-%	   sandwiched (a) and parallel displaced (b) configurations, provide
-%           a more detailed picture of the pore structure in each. The sandwiched
-%	   configuration}\label{fig:yz_correlation}
-%%MRS6: caption not finished?
-%  \end{figure} 
-%
-%  We plotted the one-dimensional pair distribution function, $g(z)$, for the
-%  phenyl rings and for carbon atoms that make up the monomer tails (Figure
-%  \ref{fig:zdf}). The plots show clear periodic maxima where layers are present.
-%  Layering is most pronounced in the head group region, however there is still a
-%  degree of layering that persists into the tail region. Using a Fourier
-%  transform on $g(z)$ from the head groups, we see that sandwiched configuration
-%  layers stack 4.39 \AA~apart while parallel displaced configuration layers stack
-%  4.38 \AA~apart. Both stacking distances are in agreement with those observed
-%  in the simulated XRD patterns.
-%
-%  %MRS6: do you need both the 2D and 1D correlation functions?
-%  \begin{figure}
-%        \centering
-%        \begin{subfigure}{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
-%                \caption{}\label{fig:zdf_layered}
-%        \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
-%                \caption{}\label{fig:zdf_offset}
-%        \end{subfigure}
-%	\caption{We support the existence of layers with the observance of
-%		clear periodic maxima in the $z$-direction pair distribution functions of the
-%		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
-%		displaced configurations. The extent to which we consider a system to be
-%		layered is based on the magnitude of the deviation of the periodic maxima from
-%		the average number density. The sandwiched configuration possesses a higher
-%		degree of layering than the parallel displaced configuration and, in both
-%		cases, the head group region has a higher degree of layer partitioning than the
-%		tail region. (See Supporting information for detailed definitions of the head
-%		group and tail regions)}\label{fig:zdf}
 %  \end{figure}

### 2018-08-09 Ben_Manuscripts/structure_paper/Draft.tex
Minor edits
New figures

@@
   and disordered basins. What we find is that any system where $\mathit{d}=3.7$ \AA~can generally 
-  be characterized as being in an
-  more ordered basin, and any system where $\mathit{d}=5.0$ \AA~can be characterized as a more the disordered basin.
-  Generally, when monomers are started further apart, they stay further apart than systems where
-  monomers are started closer together (see Table~\ref{table:correlation_length}). Because of the
-  extra space between stacked monomers, monomer head groups have more rotational freedom. We
-  quantified the ordering of the head groups using the nematic order parameter (see section S-\ref{S-method:nematic_order} for details of calculation). 
-  Disordered basin systems have a lower nematic order parameter (meaning they are more disordered) 
-  than ordered basin systems.
+  be characterized as being in a more ordered basin, and any system where $\mathit{d}=5.0$ \AA~can
+  be characterized as a more the disordered basin. Generally, when monomers are started further 
+  apart, they stay further apart than systems where monomers are started closer together 
+  (see Table~\ref{table:correlation_length}). Because of the extra space between stacked 
+  monomers, monomer head groups have more rotational freedom. We quantified the ordering of
+  the head groups using the nematic order parameter (see section S-\ref{S-method:nematic_order}
+  for details of calculation). Disordered basin systems have a lower nematic order parameter 
+  (meaning they are more disordered) than ordered basin systems.
 
@@
   disordered sandwiched and disordered parallel displaced configurations stack
-  $\sim$4.87 and 4.94 \AA~apart respectively, which is ca. 1.2~\AA further apart
+  $\sim$~4.87 and 4.94 \AA~apart respectively, which is ca. 1.2~\AA~further apart
   than suggested by experiment. 5 column-per-pore systems stack, at a maximum,
@@
 
-  The simulated XRD patterns of the parallel displaced configurations show an additional
-  reflection due to their helical structure. There are weak horizontal reflections near $|q_z|= 
-  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
-  $q_r = 0~\AA^{-1}$ so it does not necessarily appear for the same reason as R-double. 
-  This type of pattern is characteristic of a helix~\cite{watson_structure_1953}, as the 
-  head groups in the parallel displaced configuration are arranged in a helix.
-  It is possible that these reflections contribute to the diffuse reflections that connect
-  R-spots and R-double in the experimental pattern.
+  The simulated XRD patterns of the parallel displaced configurations show additional
+  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
+  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
+  for the same reason as R-double. It is possible that parallel displaced monomers contribute
+  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.
+
+  %  This type of pattern is characteristic of a helix~\cite{watson_structure_1953}, as the 
+  %  head groups in the parallel displaced configuration are arranged in a helix.
 
@@
   agrees with experiment. There is no R-double intensity to be measured. Figures
-  are provided in section S-\ref{S-section:xrd_intensities} to make these measurements clear.
+  are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements.
 
@@
   %gave rise to the feature. 
-  R-spots originates from the monomer tails. By removing all non-tail atoms from 
-  the trajectory and simulating a diffraction pattern with the remaining atoms, 
-  we were able to isolate the cause of the spots to the tails 
-  (Figure~\ref{fig:tails_rzplot}).
-
-  The tails pack together hexagonally. We plotted the center of mass of the 
+  Although the monomer tails do not tilt, R-spots still originates from the 
+  them. By removing all non-tail atoms from the trajectory and simulating a
+  diffraction pattern with the remaining atoms, we were able to isolate the
+  cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
+
+  %BJC9: I think Matt gets confused here. I put a more detailed explanation in 
+  % the supplemental information. Do you think that's enough, or should I add
+  % to this figure?
+  The tails pack together hexagonally. We plotted the center of masses of the 
   first four tail atoms of each tail originating from each head group 
   (Figure \ref{fig:centroids}). We measured the angle between each center of
-  mass and its nearest neighbors with respect to the $xy$ plane of the membrane. 
-  We see distinct peaks in the distribution of these angles located ca. 
-  $-60\degree$, $0\degree$, and $60\degree$ which is consistent with a 
-  hexagonally packed configuration (Figure~\ref{fig:layered_tails}). This 
-  ordering dies off at the tail ends, where there is more space to fill 
-  causing them to pack nearly isotropically (See supporting information).
+  mass and its nearest neighbor center of masses with respect to the $xy$ 
+  plane of the membrane. We see distinct peaks in the distribution of these 
+  angles located ca. $-60\degree$, $0\degree$, and $60\degree$ which is 
+  consistent with a hexagonally packed configuration 
+  (Figure~\ref{fig:layered_tails}). This ordering dies off at the tail ends,
+  where there is more space to fill causing them to pack nearly isotropically.
+  See Section~S-\ref{S-tail_packing} for a more detailed explanation of the 
+  calculation and packing distributions generated from different sections of
+  the tails.
 
@@
 
-  % BJC9: This still needs to be worked out. Rest of section should still hold up
-  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
-  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
-  The FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the
-  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
-  experimental data is best fit with a Lorentzian function while the simulated
-  patterns are best fit using a Gaussian function. The simulated spectra do not
-  incorporate the effects of finite domain sizes, pressure broadening and
-  instrumental broadening which would alter the peak shape. In the absence of
-  these and other peak broadening effects, the experimental peak would actually
-  be narrower, further increasing the discrepancy with simulation.
+  The peak shape of the $q_r$ cross-section of R-$\pi$ is qualitatively different
+  from experiment (Figures~\ref{fig:exp_rsection_fit} and~\ref{fig:sim_rsection_fit}).
+  We use simulated XRD generated from the ordered parallel displaced configuration
+  as an example in Figure~\ref{fig:rpi_exp_comparison}. The $q_z$ cross-section 
+  fits a Lorentzian profile relatively well, although its full width at half maximum
+  (FWHM) is 48 \% broader than the experimental cross-section 
+  (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). We attempted
+  to fit a Lorentzian profile to the $q_r$ cross-section and although the FWHM agrees
+  with experiment within error, the fit is not optimal due to the three sharp peaks
+  that appear near $q_r$ = 0.
+
+  An exact quantitative comparison between experiment and simulation is not feasible. 
+  Experimental peaks broaden due to effects that we can not easily simulate such
+  as finite size crystalline domains and instrumental resolution. In our simulated
+  XRD patterns, the system size imposes limitations on the resolution, which makes
+  it difficult to reliably fit peaks. This is especially problematic when comparing
+  the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental FWHM 
+  (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
+  Additionally, we model each atom with a Gaussian sphere of electron density. 
+  The true electronic structure is likely much more complicated. The subsequent
+  discussion primarily serves to demonstrate how we can qualitatively change the
+  peak shapes to be in better agreement with experiment.
+
+% BJC9: old version of above paragraph
+%  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
+%  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
+%  The FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the
+%  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
+%  experimental data is best fit with a Lorentzian function while the simulated
+%  patterns are best fit using a Gaussian function. The simulated spectra do not
+%  incorporate the effects of finite domain sizes, pressure broadening and
+%  instrumental broadening which would alter the peak shape. In the absence of
+%  these and other peak broadening effects, the experimental peak would actually
+%  be narrower, further increasing the discrepancy with simulation.
 
@@
   \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
+  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
+  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
   \includegraphics[width=\textwidth]{exp_zsection_fit.png}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
-  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
   \includegraphics[width=\textwidth]{sim_zsection_fit.png}
-  \caption{FWHM = 0.194 $\pm$ 0.013 $\AA^{-1}$}\label{fig:sim_zsection_fit}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
-  \caption{FWHM = 0.962 $\pm$ 0.010 $\AA^{-1}$}\label{fig:sim_rsection_fit}
+  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
   \end{subfigure}
   \caption{
-  In experiments ((a) and (b)), (a), R-$\pi$ broadens in the $q_z$ direction
-  with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when fit with a Lorentzian
-  function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792
-  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. In our simulations
-  ((c) and (d)), (c) the FWHM of R-$\pi$ in the $q_z$ direction is 0.194 $\pm$
-  0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width of
-  experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01
-  $\AA^{-1}$ when fit with a Gaussian function, about 20 \% larger than
-  experiment. Note that the large spike in the center is not included in the
-  fit.}\label{fig:rpi_exp_comparison}
+%  There are clear qualitative differences between the experimental WAXS pattern 
+%  ((a) and (c)) and the simulated XRD pattern resulting from simulations 
+%  of the ordered parallel displaced configuration ((b) and (d)). 
+  We compared the experimental WAXS pattern ((a) and (c)) to the simulated XRD
+  pattern resulting from simulations of the ordered parallel displaced 
+  configuration ((b) and (d)). The $q_r$ cross-section of R-$\pi$ ((a) and (b))
+  is qualitatively different between experiment (a) and simulation (b). We fit
+  Lorentzian profiles to each peak and the FWHM of the simulated pattern agrees
+  with experiment within error, however the fit to the simulated data is 
+  obscured by the three sharp peaks which appear near $q_r$ = 0. The $q_z$ 
+  cross-sections of R-$\pi$ ((c) and (d)) are qualitatively similar. Each fits
+  a Lorentzian profile well, however the FWHM of the simulated cross-section (d)
+  is 48 \% larger than the experimental cross-section.}\label{fig:rpi_exp_comparison}
   \end{figure}
@@
   forcefield and initial configurations could affect the intensity and shape of
-  R-$\pi$. We assessed each using a
-  simplified model. Our simplified model represents each monomer head group as a
-  single point and places them in either a parallel displaced or sandwiched
-  configuration. We chose to explore the influence of thermal noise in each
-  dimension, the effect of $z$-direction distance correlations between scatterers
-  within columns, as well as correlation between columns since these are the
-  variables we believe have the largest influence on peak shape and intensity.
-  %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.
+  R-$\pi$. We assessed each using a simplified model. Our simplified model 
+  epresents each monomer head group as a single point and places them in either
+  a parallel displaced or sandwiched configuration. We chose to explore the 
+  influence of thermal noise in each dimension, the effect of $z$-direction 
+  distance correlations between scatterers within columns, as well as correlation
+  between columns since these are the variables we believe have the largest 
+  influence on peak shape and intensity.
 
@@
   disorder to consider: thermal motion of atoms and quenched disorder which is
-  created by rapid structural rearrangement during early equilibration and is
-  largely locked into place for the remainder of the simulation. The latter has
-  important implications for the reproducibility of this work since both initial
-  configurations and initial velocity randomization can
-  lead to different quenched configurations. We measured thermal disorder by
-  calculating the standard deviation of the distribution of head group center of
-  mass positions from their average positions. We measured quenched disorder by
-  calculating the standard deviation of the distribution of head group center of
-  masses from their idealized average positions. In the $z$-direction, we
-  measured the deviation of the head group center of masses from an equally
-  spaced column of head groups. In the $xy$ plane, we calculated the deviation in
-  radial position from the pore center and the angular deviation from equally
-  spaced points surrounding the pore center. This method for calculating 
-  quenched order inherently includes thermal disorder. The values measured for
-  each system and type of disorder are given in Table~\ref{table:quenched_disorder}.
-
-  The intensity of R-$\pi$ can be calculated from a single trajectory of
-  uncorrelated configurations rather than from the average of multiple correlated
-  trajectories. Theoretically, in order to mimic the simulated system, we should
-  build an initial configuration which has the same amount of quenched disorder
-  as our simulations and then create a trajectory to which we add thermal
-  noise to each subsequent frame. In this scenario, the positions of each scatterer
-  will not change in a way that significantly affects the intensity of R-$\pi$
-  since most of its character is defined by the far more disordered initial configuration.
-  To uncover the expected intensity of R-$\pi$, we would need to average over many
-  such trajectories. To bypass this expensive calculation, we instead calculate the
+  created by rapid structural rearrangement during early equilibration and 
+  is largely locked into place for the remainder of the simulation. The latter
+  has important implications for the reproducibility of this work since both 
+  initial configuration and initial velocity randomization can lead to 
+  different quenched configurations. We measured thermal disorder by
+  calculating the standard deviation of the distribution of head group center 
+  of mass positions from their average positions. We measured quenched 
+  disorder by calculating the standard deviation of the distribution of head
+  group center of masses from their idealized average positions. In the 
+  $z$-direction, we measured the deviation of the head group center of masses
+  from an equally spaced column of head groups. In the $xy$ plane, we 
+  calculated the deviation in radial position from the pore center and the
+  angular deviation from equally spaced points surrounding the pore center.
+  This method for calculating quenched order inherently includes thermal 
+  disorder. The values measured for each system and type of disorder are given
+  in Table~\ref{table:quenched_disorder}.
+
+  The expected maximum intensity of R-$\pi$ can be calculated from a single
+  trajectory of uncorrelated configurations rather than from the average of 
+  multiple trajectories of correlated frames. Theoretically, in order to
+  mimic the simulated system, we should build an initial configuration which 
+  has the same amount of quenched disorder as our simulations and then create
+  a trajectory to which we add thermal noise to each subsequent frame. In this
+  scenario, the positions of each scatterer will not change in a way that 
+  significantly affects the intensity of R-$\pi$ since most of its character 
+  is defined by the far more disordered initial configuration. To uncover the
+  expected intensity of R-$\pi$, we would need to average over many such 
+  trajectories. To bypass this expensive calculation, we instead calculate the
   R-$\pi$ intensity from a trajectory consisting of many independent initial 
-  configurations. This simulates the long time scales over which we expect columns
-  to sample many configurational states. %We use the latter method for the remainder of
-%  this section since we can extract the trends we need using a single trajectory at
-%  a fraction of the computational cost.
-
- %BJC9 : Could show some number like the following
-%  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this (1st way mentioned above)
-%  way was 16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000
-% initial configurations, the intensity of R-$\pi$ is 16.42, in close agreement
-%  with the mean of 40 simulations.
+  configurations. This simulates the long time scales over which we expect 
+  columns to sample many configurational states. %We use the latter method 
+  %for the remainder of this section since we can extract the trends we 
+  %need using a single trajectory at a fraction of the computational cost.
 
@@
 
-  The correlation length of vertically stacked scatterers in our simulations
+  The correlation length of vertically stacked scatterers in our atomistic simulations
   are in reasonable agreement with experiment. Since it is not feasible for us to
@@
   distribution function, $g(z)$, for the centers of mass of monomer phenyl rings
-  (Figure~\ref{fig:correlation}). 
+  (Figure~\ref{fig:correlation}). In order to calculate $g(z)$, we averaged all
+  $z$-slices of the 3D correlation function within 2.1 \AA of $g(0, 0, z)$. In this
+  way we are trying measure correlation between head groups within the same column.
   %We used this 
@@
   the closest agreement with experiment (Table~\ref{table:correlation_length}).
-  We calculated the correlation length of each system using
+  Note that its correlation length ($L$ = 14.5 \AA) is larger than what we would 
+  expect by inverting the FWHM of the $q_z$ cross-section of R-$\pi$ shown in 
+  Figure~\ref{fig:sim_zsection_fit} ($L$ = 1 / 0.163 = 6.1 \AA). The reason is
+  likely a combination of artificial broadening caused by the overlap of 
+  R-alkanes and R-$\pi$ as well as errors in the fit due to low simulated 
+  XRD resolution. We calculated the correlation length of each system using 
   Equation~\ref{eqn:decaying_exponential}. We could not extract a reliable 
@@
 
-  Increased thermal noise in the $z$-direction causes a drop in the intensity
+  Increased thermal noise in the $z$-direction will reduce the intensity
   of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
-  thermal noise of our parallel displaced simple system in the $z$-direction by
+  thermal noise of our simple parallel displaced system in the $z$-direction by
   12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of 
@@
   it is not feasible for columns in the parallel displaced configuration, as we
-  have set them up, to move past each other. The trends seen above apply to both
-  the sandwiched and parallel displaced systems. 
-  %BJC9: ^need to prove that in supplemental?  
-  Allowing columns to move
-  independently smooths out the $q_r$ cross-section
-  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in
-  sharp peaks. The intensity of R-$\pi$ decreases with increasing column
-  independence. We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$
-  versus when $f=0$. It is likely that the discrepancy between the intensity of 
-  R-$\pi$ generated from our simulations versus experiment is primarily due
-  to highly correlated columns in our initial configurations.
+  have set them up, to move past each other. When $f = 1$, the columns move 
+  independently and the $q_r$ cross-section smooths out 
+  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp
+  peaks. The intensity of R-$\pi$ decreases with increasing column independence.
+  We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$ versus when
+  $f=0$. It is likely that the discrepancy between the intensity of R-$\pi$ 
+  generated from our simulations versus experiment is primarily due to highly 
+  correlated columns in our initial configurations.
 
@@
           relatively smooth.}\label{fig:column_displacement}
+  \end{figure}
+
+  The columns in the simulated system are highly correlated. If the columns were
+  uncorrelated, $g(z)$ of the ordered sandwiched system would very closely resemble 
+  Figure~\ref{fig:z_correlation_sandwich} when we average all $z$-slices of the
+  3D correlation function. When we include all $z$-slices in $g(z)$ for our system,
+  the function shows oscillatory behavior and the correlation length nearly triples
+  to 12.41 $\pm$ 0.69 \AA. (Figure~\ref{fig:z_correlation_fullbox}). Since all 
+  columns in our initial configuration are started at the same $z$-coordinate, 
+  $g(z)$ on average exhibits correlation of head groups with other head groups
+  within the same column, with head groups in other columns within the same pore, 
+  and with head groups in different pores.
+
+  %BJC9: Note that the magnitude of the correlation function is much lower than 
+  % in figure 10a. That's because many of the z-slices are zero when you include
+  % all of them.
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.png}
+  \caption{When we average all $z$-slices of the 3D correlation function, the 
+  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
   \end{figure}

### 2018-08-09 Ben_Manuscripts/structure_paper/supporting_information.tex
Figure updates
New figures

@@
-\documentclass[journal=jpcbfk,manusciprt=article]{achemso}
+%\documentclass[journal=jpcbfk,manuscript=article]{achemso}
+\documentclass{article}
 
@@
 \usepackage{amsmath} 
-%\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
+\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
 \usepackage{siunitx}
@@
 
-\SectionNumbersOn
+%\SectionNumbersOn
 
 \externaldocument[M-]{draft}
-%MRS8: can use document class here - looks weird with title/authors as written.
 \title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
@@
 
-%  \bibliographystyle{ieeetr}
+  \bibliographystyle{ieeetr}
   \graphicspath{{./figures/}}  % put all the figures here
@@
 	  \toprule
-          %MRS8: nm to aa conversion error?
 	  Initial Pore Radius & Equilibrated Pore Radius \\
 	  \midrule
-	  % BJC: to be updated once simulations are run out long enough
-	  2.5 \AA & $0.40 \pm 0.01$ \AA \\
-	  5 \AA   & $0.42 \pm 0.01$ \AA \\ % final result
-	  8 \AA   & $0.69 \pm 0.01$ \AA \\
+	  2.5 \AA & $4.0 \pm 0.1$ \AA \\
+	  5 \AA   & $4.2 \pm 0.1$ \AA \\
+	  8 \AA   & $6.9 \pm 0.1$ \AA \\
 	  \bottomrule
@@
 %  \end{figure}
-
-  \begin{figure}[!htb]
-        \centering
-%        \begin{subfigure}{0.45\textwidth}
-%                \centering
-%                \hspace{-1cm}
-%                \vspace{1cm}
-%                \includegraphics[width=\textwidth,scale=2]{tails_topview.png}
-%                \caption{}\label{fig:tails_topview}
-%        \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{tails_rzplot.png}
-%                \caption{}\label{fig:tails_rzplot}
-%        \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-                \includegraphics[width=0.5\textwidth]{centroids_box.png}
-		\caption{Monomer tails pack together hexagonally. The centroid
-			of each tail is visualized as a blue sphere. The centroids are calculated based
-			on the red atoms in Figure~\ref{fig:monomer_color_coded}. The red sphere
-			highlights an example of an alkane tail centroid with its nearest neighbors
-			(green spheres) surrounding it in a hexagonal pattern.}\label{fig:centroids}
-%        \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{angles_traj_layered.png}
-%                \caption{}\label{fig:angle_distribution}
-%        \end{subfigure}
-%        \caption{(a) The trajectory can be stripped of all atoms except carbon
-%        atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
-%        still gives rise to R-spots. (c) Finding the center of mass and visualizing
-%        their coordinates reveals the hexagonal-like packing of the tails. (d) The
-%        distribution created by measuring the angle between each centroid (e.g. red
-%        in (c)) and its nearest neighbors (e.g. green in (c)) with respect to the xy
-%        plane has distinct spikes near 30\degree, which is consistent with the location
-%        of R-spots}\label{fig:tail_packing}
+  \section{Tail organization}
+
+  In order to understand the origin of R-spots, we looked for ordering among
+  the tails. We divided the tail into three sections: tail fronts, tail 
+  middles and tail ends. The sections are illustrated in 
+  Figure~\ref{fig:tail_sections}.
+
+  We plotted the center of masses of each tail section and measured the angle 
+  between each center of mass and its nearest neighbor center of masses of the
+  same tail section. For example, Figure~\ref{fig:centroids} shows a 3D plot of
+  the center of masses of each tail front. We wanted to know average location
+  of nearest neighbors to each center of mass. The red bead in 
+  Figure~\ref{fig:centroids} is a randomly selected center of mass. The
+  green beads are the nearest neighbor center of masses to the red bead. We
+  measured the angle between the red bead and each green bead with respect to
+  the $xy$ plane. We repeated the same calculation for each center of mass at
+  each simulation frame and were able to plot the average distribution shown
+  in Figure~\ref{fig:tail_fronts}. We repeated the calculation for the tail
+  middles (Figure~\ref{fig:tail_middles}) and the tail ends 
+  (Figure~\ref{fig:tail_ends}). The amount of order decreases as we explore
+  packing of tails farther from the head group.
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{tail_sections}
+  \caption{We divided the tail into three regions: tail-fronts (blue), 
+  tail-middles (green) and tail-backs (red).}\label{fig:tail_sections}
+  \end{figure}
+
+  \begin{figure}[!htb]
+        \centering
+        \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{centroids.png}
+		\caption{}\label{fig:centroids}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{hexagonal_tail_packing.png}
+        \caption{}\label{fig:tail_fronts}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{hexagonal_tail_packing_middles.png}
+        \caption{}\label{fig:tail_middles}
+        \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{hexagonal_tail_packing_ends.png}
+        \caption{}\label{fig:tail_ends}
+        \end{subfigure}
+        \caption{Monomer tails pack together hexagonally. (a) The center of mass
+        of each tail-front (See Figure~\ref{fig:tail_sections}) is visualized as
+        a blue sphere. The red sphere highlights an example of a tail-front 
+        center of mass with its nearest neighbors (green spheres) surrounding it
+        in a hexagonal pattern. (b) We calculated the angle between each tail-front
+        center of mass and its nearest neighbor tail-front center of masses and 
+        plotted the distribution. There are distinct peaks ca. $-60\degree$, $0\degree$ and
+        $60\degree$ which is indicitive of hexagonal packing. (c) We repeated the 
+        same procedure outlined in (a) and (b) with the tail-middles. There is still 
+        a high degree of order. (d) We repeated the procedure again with the tail-ends.
+        There is far less order at the ends of the tails where there is more
+        space to fill.}\label{fig:tail_packing}
   \end{figure}

### 2018-08-14 Ben_Manuscripts/structure_paper/Draft.tex
Comments.

@@
   experiment in Figure~\ref{fig:XRDsim}.
-
+  %MRS10: Would be btter to lead with something describing what we found, not a caveat, just for clarity.
+Might belong better in the previous paragraph if left here, since it is a clarifying point that should be communicated, not an actual finding.
   The diffraction patterns show some noise, especially along the axis where $q_r$=0. There are
@@
   defects and domain misalignment which decreases the overall intensity.
+  %MRS10: would domain misalignment make a difference in itensity?  I though we decided it wouldnt (it would more broaden?).
+  %You can talk about how you WILL analyze the intensity diffence later on, that it doesn't need to be analyzed here.
   % MRS4: comments from Matt suggest that domain misalignment shouldn't alone be responsible for 
@@
   relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
+  %MRS10: weird transition between these two; it's a result that interrupts the discussion of methods.
   R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
-  identified spots based on visual inspection. If the spots were not easily discernible, then the 
+  identified spots based on visual inspection. 
+  %MRS10: what criteria were used?  Need to provide what was used to make the decision.
+If the spots were not easily discernible, then the 
   intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
-  R-$\pi$, since that is where it appears experimentally. The intensity of R-spots is slightly
+  R-$\pi$, as that is where it appears experimentally. The intensity of R-spots is slightly
   lower than experiment in all cases except for the ordered basin sandwiched configuration which 
-  agrees with experiment. There is no R-double intensity to be measured. Figures
-  are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements.
+  agrees with experiment. There is no R-double intensity to be measured. %MRS10: specific where no R-double intensity was measured. None of the simulations, correct?
+Figures are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements. %MRS10: Specify what figures clarify what things.  Also, use active voice in this section.
 
@@
   want answer:  
+  %MRS10: should the ``why is R-pi in not quite the right place'' be here, to have those sorts of questions more centralized?
   \begin{enumerate}
@@
   \subsubsection{The origin of R-spots}\label{section:rspots}
-
+%MRS10: I rephrased the below, check the diffs.
   In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
-  configuration at 280K. Obtaining an equilibrium structure at a precise temperature is
-  a challenge that force fields often fail to overcome. Wang et al. highlighted the 
+  configuration at 280K. Many force fields do not obtain the correct equilibrium structure at precisely the experimental temperature. Wang et al. highlighted the 
   shortcoming of some of the most popular protein force field in predicting the temperature
-  dependence of protein structural ensembles \cite{wang_building_2017}. It is possible that   % page 12
-  our membrane system, simulated at 300K, does not fully represent the true structure at 300K.
-  Lowering the temperature to 280K helped us to better resolve R-spots (Figure~\ref{fig:sandwiched280K}). 
+  dependence of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
+  our membrane system, simulated at 300K, is overly structured compared to the experimental structure at 300K.
+  We found that lowering the temperature better resolved the R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' temperature might indeed be too high, overstabilizing structure.
 %  The relative intensity 
@@
 
-  Evidence strongly suggests that the R-spots signal is not a result of alkane
+  Evidence 
+%MRS10: added
+from the simulations
+  strongly suggests that the R-spots signal is not a result of alkane
   chain tilt. Previous literature has attributed the spots in this particular
-  WAXS pattern as the product of tilted alkane chains~\cite{feng_scalable_2014}.
+%MRS10: clarified that it was THIS exact data, and not similiar images. Correct if wrong.
+WAXS 
+%pattern 
+dataset
+as the product of tilted alkane chains~\cite{feng_scalable_2014}.
   We measured the tilt angle of the alkane chains of the 280K system and showed
@@
   % to this figure?
-  The tails pack together hexagonally. We plotted the center of masses of the 
+  %MRS10: rephrased.
+  The evidence strongly suggests that R-spot pattern occurs because tails pack together hexagonally. 
+  We plotted the center of masses of the 
   first four tail atoms of each tail originating from each head group 
@@
   consistent with a hexagonally packed configuration 
-  (Figure~\ref{fig:layered_tails}). This ordering dies off at the tail ends,
+  (Figure~\ref{fig:layered_tails}). 
+  %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
+This ordering dies off at the tail ends,
   where there is more space to fill causing them to pack nearly isotropically.
@@
 
-  The peaks in the nearest neighbor angle distribution are consistent with the
+  The peaks in the nearest neighbor angle distribution due to the hexagonal packing are consistent with the
   location of R-spots. The 2D Fourier transform of a simple hexagonal array 
@@
   \subsubsection{Discrepancies between experimental and simulated R-$\pi$}\label{section:rpi}
-
-  R-$\pi$ is more intense relative to the experimental system. The difference in intensity
+  %MRS10: in the list of questions above, you just talk about intensity, but this title talks about more discrepnacies.
+It could go either way (as I mention before, there's the issue of R-pi placement, too), but it should be consistent.
+  The experimentally measured R-$\pi$ is more intense relative to the experimental system. The difference in intensity
   ranges from 3 times too high in the ordered parallel displaced system to 15 times too 
   high in the ordered sandwiched configuration (Table~\ref{table:relative_inensities_300K}).
-
-  The peak shape of the $q_r$ cross-section of R-$\pi$ is qualitatively different
+  %MRS10: should specify this is in the 300 K simulations.
+
+  The peak shape of the $q_r$ cross-section of R-$\pi$ in the simulated XRD is qualitatively different
   from experiment (Figures~\ref{fig:exp_rsection_fit} and~\ref{fig:sim_rsection_fit}).
@@
   fits a Lorentzian profile relatively well, although its full width at half maximum
-  (FWHM) is 48 \% broader than the experimental cross-section 
+  (FWHM) is 48\% broader than the experimental cross-section 
   (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). We attempted
@@
 
-  An exact quantitative comparison between experiment and simulation is not feasible. 
+  An exact quantitative comparison between experiment and simulation is not feasible for several reasons. 
   Experimental peaks broaden due to effects that we can not easily simulate such
@@
   Additionally, we model each atom with a Gaussian sphere of electron density. 
-  The true electronic structure is likely much more complicated. The subsequent
-  discussion primarily serves to demonstrate how we can qualitatively change the
-  peak shapes to be in better agreement with experiment.
+  The true electronic structure is likely much more complicated. 
+  %MRS10: modified
+  However, we can explore reasons for which differences in the simulation structure could changes the peak shapes to be in better agreement with experiment.
 
@@
 %  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
-%  The FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the
+%  The FWHM of the $q_z$ cross-section is 76\% larger than experiment and the
 %  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
@@
 %  of the ordered parallel displaced configuration ((b) and (d)). 
+    %MRS10: don't make the thesis what was done, but what the reader should know. 
   We compared the experimental WAXS pattern ((a) and (c)) to the simulated XRD
@@
   a Lorentzian profile well, however the FWHM of the simulated cross-section (d)
-  is 48 \% larger than the experimental cross-section.}\label{fig:rpi_exp_comparison}
+  is 48\% larger than the experimental cross-section.}\label{fig:rpi_exp_comparison}
   \end{figure}
@@
   forcefield and initial configurations could affect the intensity and shape of
-  R-$\pi$. We assessed each using a simplified model. Our simplified model 
-  epresents each monomer head group as a single point and places them in either
+  R-$\pi$, and assess each using a simplified model of the pore. Our simplified model 
+  represents each monomer head group as a single point and places them in either
   a parallel displaced or sandwiched configuration. We chose to explore the 
@@
 
-  As a baseline, we created a simplified model using the same amount of
+  %MRS10: somewhere in here, we need to address whether quenched and static disorder are 
+  % the same experimentally. If not the same, then it's glassy, if they are the same, then 
+  % we are making the assumption that the the timescales of motion of that noice are > 1 microsecond but < 1 second.
+  We created a simplified baseline model using the same amount of
   disorder present in our atomistic simulations. There are two sources of
@@
   is largely locked into place for the remainder of the simulation. The latter
-  has important implications for the reproducibility of this work since both 
+  has important implications 
+  %MRS10: which are the important implications?
+for the reproducibility of this work since both 
   initial configuration and initial velocity randomization can lead to 
@@
 
+  %MRS10: this is more of a methodological thesis than is ideal. Can you make it more about what we are learning, or at least what was done and the reasoning?
   The expected maximum intensity of R-$\pi$ can be calculated from a single
@@
 
+  %MRS10: again, more of a methodolgical thesis.  Will not be clear to the reader what they are 
+  % expecting to learn, which is the difference in the simulation that could explain the differences in the spectra.
+  % I'm thinking some of this should be in the supporting info.  Maybe not, if key enough, but it should still be in support of the conclusion. 
   When we simulated the diffraction pattern of a parallel displaced simple
@@
   cross-section (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in
-  experiment. Additionally, there is a near 20 \% increase in the maximum
+  experiment. Additionally, there is a near 20\% increase in the maximum
   intensity of R-$\pi$ when the distances between scatterers are correlated.
@@
   (Figure~\ref{fig:correlation}). In order to calculate $g(z)$, we averaged all
-  $z$-slices of the 3D correlation function within 2.1 \AA of $g(0, 0, z)$. In this
+  $z$-slices of the 3D correlation function within 2.1 \AA~of $g(0, 0, z)$. In this
   way we are trying measure correlation between head groups within the same column.
@@
   \end{subfigure}  
+  %MRS10: should say something here about whether this is consistent or not with experiement (and why/why not)
+  %MRS10: maybe include correlation lengths as well calculated from these, and compare to experiment?
+I know it's in the table as well, but seems missing here.
+1D correlation functions are given, but not how that data proves central points.
   \caption{1D correlation functions of the center of masses of aromatic head
@@
   sandwiched and parallel displaced configurations respectively. The distance
+  %MRS10: OK this is finally addressed here, but it it's sort of buried in the middle of a paragraph, and not laid out as an outlined point, whereas most readers would ask about it early.
   between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all
@@
   increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
-  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$
+  $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
   decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
@@
   intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
-  diffraction patterns smooths out. We created simple systems with varying
+  diffraction patterns smooths out. 
+  This is shown by creating 
+  simple systems 
+  %MRS10: simple systems is not very exact. Point scatters that represent the head groups?
+  with varying
   amounts of association between columns. In the low limit, the center of mass
-  of columns are situated at the same $z$-coordinate. This is how all simple
+  of columns are situated at the same $z$-coordinate. 
+  %MRS10: unnecessary line?
+  This is how all simple
   systems have been created up to this point. We allow increasing independence of
@@
   Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
-  cross-section of R-$\pi$ to decrease. Using a system with uncorrelated columns,
+  cross-section of R-$\pi$ to, somewhat counterintuitively, to decrease. Using a system with uncorrelated columns,
   we modified the disorder in both the $r$ and $\theta$ directions by multiplying
   their values by a factor of 0.5 and 2 (Figure~\ref{fig:qy_fwhm}). When we cut
-  the noise in half, the FWHM increases by 88 \%. When we double the noise, the
-  FWHM decreases by 51 \%.
+  the noise in half, the FWHM increases by 88\%. When we double the noise, the
+  FWHM decreases by 51\%.
 
@@
 
+  %MRS10: Maybe rephrases; rather than talking about building a better
+  %model, you can summarize the differences that could explain the discrepancy between experiment and simulation.
   We can use what we learned above in order to construct a better model,
@@
 
+%MRS10: I wonder if it would be better to lead with what we think IS the answer, and then rule out other effects.  
   We can produce R-double if we rotate monomers with respect to vertically adjacent monomers.
@@
 %  \end{subfigure}
-%	\caption{Adding 1 wt \% water to the ordered basin dry systems causes an increase in the intensity
+%	\caption{Adding 1 wt\% water to the ordered basin dry systems causes an increase in the intensity
 %	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
@@
 %  The appearance of R-double may be due to increased order of the pores. The first
-%  peak of the correlation function, $g(z)$, is approximately 30 \% larger in the 
+%  peak of the correlation function, $g(z)$, is approximately 30\% larger in the 
 %  solvated versus dry configuration (Figure~\ref{fig:solvated_correlation_overlay}).
@@
   We calculated the ionic conductivity of the parallel displaced configuration in
-  the ordered basin with 1 wt \% water since we believe its structure is the 
+  the ordered basin with 1 wt\% water since we believe its structure is the 
   closest match to experiment. Our model estimates the ionic conductivity within

### 2018-08-14 Ben_Manuscripts/structure_paper/Draft.tex
reorganization

@@
 
-  \subsection{Density of monomers around pores}
+  \subsection{Density of monomers around pores}\label{section:mon_per_pore}
 
@@
   basins. We generated simulated patterns using the equilibrated portion of each 
-  simulation trajectory. The patterns for all structures are shown and compared to
-  experiment in Figure~\ref{fig:XRDsim}.
-  %MRS10: Would be btter to lead with something describing what we found, not a caveat, just for clarity.
-Might belong better in the previous paragraph if left here, since it is a clarifying point that should be communicated, not an actual finding.
-  The diffraction patterns show some noise, especially along the axis where $q_r$=0. There are
-  two main reasons for this noise. First is that we angle averaged the 3D structure factor 
-  (see section~\ref{method:xrd}) which inherently gives less data as $q_r$ approaches 0. Second, 
-  our simulations are not long enough to sample enough truly independent configurations within
-  their respective metastable basins. By sampling more uncorrelated equilibrium configurations,
-  we can suppress some of the noise (See section S-\ref{S-section:xrd_noise}).
-
+  simulation trajectory. The simulated diffraction patterns have some noise, especially
+  along the $q_z$ axis at $q_r$=0. There are two main reasons for this noise. First
+  is that we angle averaged the 3D structure factor (see section~\ref{method:xrd})
+  which inherently gives less data as $q_r$ approaches 0. Second, we hypothesize that 
+  the more important issue is that our simulations are not long enough to sample 
+  enough truly independent configurations within their respective metastable basins
+  (See section~\ref{section:slow_dynamics}). By sampling more uncorrelated equilibrium
+  configurations, we can suppress some of the noise (See section S-\ref{S-section:xrd_noise}
+  for a detailed example of this effect). The simulated patterns generated for all systems
+  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
+
+  % BJC10: to be reformatted : add captions. Maybe shift experimental pattern to (a)
+  % BJC10: be more terse in main caption. Add references to sections
   \begin{figure}[!htb]
@@
 
-  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
-  R-pores appear in the expected location. R-pores is more intense than experiment, likely
-  because we are simulating a near perfect, infinite hexagonal array. The real system has 
-  defects and domain misalignment which decreases the overall intensity.
+  The simulated XRD patterns show moderate agreement with experiment. There 
+  are key qualitative and quantitative differences between the experimental and simulated
+  locations and intensities of each major reflection. We measured the intensity and location
+   of each simulated reflection relative to its experimental counterpart 
+  (Table~\ref{table:relative_inensities_300K}). Our methods for measuring the intensity of
+  each reflection are presented in section S-\ref{S-section:xrd_intensities}. We have
+  devoted individual subsections to explain each major reflection. We start with relatively 
+  uncomplicated analyses of experimentally-similar reflections:
+  %BJC10: Could make the following more descriptive.
+For example : "The location of R-alkanes", "The intensity of R-pores", "The origin of R-spots", "The shape and intensity of R-pi", "The origin of R-double".
+  \begin{itemize}
+  	\item R-alkanes (section~\ref{section:ralkanes})
+  	\item R-pores (section~\ref{section:rpores})
+  \end{itemize}
+  and then move onto more complicated explanations of those reflections whose characteristics
+  do not match, or have not been fully explained by experiment:
+  \begin{itemize}
+  	\item R-spots (section~\ref{section:rspots})
+  	\item R-$\pi$ (section~\ref{section:rpi})
+  	\item R-double (section~\ref{section:rdouble})
+  \end{itemize}
+
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{c|cccccccccc}
+%  \toprule
+% 		   & \multicolumn{5}{c}{Configuration} \\
+%  \hline
+%           &\multicolumn{2}{c}{}            & \multicolumn{2}{c}{}          & \multicolumn{2}{c}{Parallel} & \multicolumn{2}{c}{Disordered} & \multicolumn{2}{c}{Disordered}         \\
+%           & \multicolumn{2}{c}{Experiment} & \multicolumn{2}{c}{Sandwiched} & \multicolumn{2}{c}{Displaced} & \multicolumn{2}{c}{Sandwiched}  & \multicolumn{2}{c}{Parallel Displaced} \\
+%  Reflection & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) \\
+%  \midrule
+%  R-alkanes  & 1.0  & 1.4  & 1.0  & 1.4 & 1.0 & 1.4 & 1.0 & 1.4 & 1.0 & 1.4  \\  
+%  R-spots    & 1.3  & 1.4  & 1.3  & 1.4 & 1.2 & 1.4 & 1.1 & 1.4 & 1.2 & 1.4  \\
+%  R-$\pi$    & 2.8  & 1.7  & 44.0 & 1.4 & 7.7 & 1.4 & 8.4 & 1.4 & 10.1& 1.4  \\
+%  R-double   & 0.9  & 0.85 & --   &  -- & --  & --  & --  & --  &  -- & --   \\ 
+%  \bottomrule
+%  \end{tabular}
+%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
+%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
+%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
+%  does not appear in any patterns, and thus has no measurable intensity.}
+%  \label{table:relative_inensities_300K} 
+%  \end{table}
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{c|ccccc}
+  \toprule
+ 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
+  \hline
+             &            &            & Parallel  & Disordered & Disordered         \\
+  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
+  \midrule
+  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\
+  R-pores    & 12.3       &  49.5      &  54.0     & 50.8       & 53.4               \\
+  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
+  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
+  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
+  \hline
+   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
+  \hline
+             &            &            & Parallel  & Disordered & Disordered         \\
+  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
+  \midrule
+  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
+  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
+  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
+  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
+  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
+  \bottomrule
+  \end{tabular}
+  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
+  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
+  than experiment and R-spots reflections that are slightly lower than experiment. R-double
+  does not appear in any patterns, and thus has no measurable intensity.}
+  \label{table:relative_inensities_300K} 
+  \end{table}
+
+%    \begin{table}[h]
+%  \centering
+%  \begin{tabular}{c|ccccc}
+%  \toprule
+% 		   & \multicolumn{5}{c}{Configuration} \\
+%  \hline
+%             &\multicolumn{2}{c}{}     &            & Parallel  & Disordered & Disordered         \\
+%  Reflection & \multicolumnExperiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
+%  \midrule
+%  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
+%  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
+%  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
+%  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
+%  \bottomrule
+%  \end{tabular}
+%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
+%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
+%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
+%  does not appear in any patterns, and thus has no measurable intensity.}
+%  \label{table:relative_inensities_300K} 
+%  \end{table}
+
   %MRS10: would domain misalignment make a difference in itensity?  I though we decided it wouldnt (it would more broaden?).
@@
   % effects.
-  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
-  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
-  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
-  maximum at $q_z < 1.5~\AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
-  rather than 3.7 \AA. R-double does not appear in any of the patterns.
+%  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
+%  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
+%  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
+%  maximum at $q_z < 1.5~\AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
+%  rather than 3.7 \AA. R-double does not appear in any of the patterns.
 
@@
 
-  The simulated XRD patterns of the parallel displaced configurations show additional
-  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
-  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
-  for the same reason as R-double. It is possible that parallel displaced monomers contribute
-  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.
-
   %  This type of pattern is characteristic of a helix~\cite{watson_structure_1953}, as the 
@@
 
-  We quantified the numerical discrepancies present when comparing the relative intensities
-  of each reflection of interest between experimental and simulated patterns. 
-  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
-  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
-  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
-  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
-  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
-  %MRS10: weird transition between these two; it's a result that interrupts the discussion of methods.
-  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
-  identified spots based on visual inspection. 
-  %MRS10: what criteria were used?  Need to provide what was used to make the decision.
-If the spots were not easily discernible, then the 
-  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
-  R-$\pi$, as that is where it appears experimentally. The intensity of R-spots is slightly
-  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
-  agrees with experiment. There is no R-double intensity to be measured. %MRS10: specific where no R-double intensity was measured. None of the simulations, correct?
-Figures are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements. %MRS10: Specify what figures clarify what things.  Also, use active voice in this section.
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{c|ccccc}
-  \toprule
- 		   & \multicolumn{5}{c}{Configuration} \\
-  \hline
-             &            &            & Parallel  & Disordered & Disordered         \\
-  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
-  \midrule
-  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
-  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
-  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
-  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
-  \bottomrule
-  \end{tabular}
-  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
-  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
-  than experiment and R-spots reflections that are slightly lower than experiment. R-double
-  does not appear in any patterns, and thus has no measurable intensity.}
-  \label{table:relative_inensities_300K} 
-  \end{table}
-  %BJC5: Bold font is caused by achemso document type
-  %MRS7: huh.
-  %BJC6: yea, specifically the one for j phys chem B. I compiled with a different document type and the captions looked normal
-  There are clear differences between simulated and experimental results that must be addressed
-  and justified. We will explore the possible origin of select experimental reflections and form 
-  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
-  want answer:  
-  %MRS10: should the ``why is R-pi in not quite the right place'' be here, to have those sorts of questions more centralized?
-  \begin{enumerate}
-	\item What is the origin of R-spots?
-  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
-  	\item What is the origin of R-double?
-  \end{enumerate}
+%  We quantified the numerical discrepancies present when comparing the relative intensities
+%  of each reflection of interest between experimental and simulated patterns. 
+%  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
+%  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
+%  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
+%  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
+%  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
+%  %MRS10: weird transition between these two; it's a result that interrupts the discussion of methods.
+%  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
+%  identified spots based on visual inspection. 
+%  %MRS10: what criteria were used?  Need to provide what was used to make the decision.
+%If the spots were not easily discernible, then the 
+%  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
+%  R-$\pi$, as that is where it appears experimentally. The intensity of R-spots is slightly
+%  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
+%  agrees with experiment. There is no R-double intensity to be measured. %MRS10: specific where no R-double intensity was measured. None of the simulations, correct?
+%Figures are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements. %MRS10: Specify what figures clarify what things.  Also, use active voice in this section.
+
+%  There are clear differences between simulated and experimental results that must be addressed
+%  and justified. We will explore the possible origin of select experimental reflections and form 
+%  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
+%  want answer:  
+%  %MRS10: should the ``why is R-pi in not quite the right place'' be here, to have those sorts of questions more centralized?
+%  \begin{enumerate}
+%	\item What is the origin of R-spots?
+%	\item How can we modify our simulations to account for the discrepancies between the experimental and simulated R-$\pi$ peak.
+%  	\item What is the origin of R-double?
+%  \end{enumerate}
 
@@
 
+  \subsubsection{R-alkanes}\label{section:ralkanes}
+
+  R-alkanes appears close to its expected location. In all cases, the maximum intensity
+  of R-alkanes appears at a $|\mathbf{q}|$ value slightly higher than experiment. 
+  We expect that the exact location of R-alkanes will not be perfect in our simulations
+  since the simulated diffraction patterns are interpolated between a finite number of
+  bins in each frequency dimension. We can achieve higher resolution with a larger
+  system size, however we are satisfied with the packing distances shown by our simulations.
+  %BJC10: I could integrate a 3D correlation function to get a better value
+
+  We believe that R-alkanes is the experimental feature most likely to be reproduced by
+  our simulations. For this reason we normalized the experimental and simulated diffraction
+  patterns so that the average intensity within the R-alkanes is equal to 1.
+
+  \subsubsection{R-pores}\label{section:rpores}
+
+   R-pores is about 4 times more intense than experiment in all simulated systems. 
+   %BJC10: trying to come up with a good explanation.
+
+   We are not concerned with exactly reproducing the intensity of R-pores since it is a 
+   product of long distance correlation between pores. We are primarily concerned with
+   the structure within pores which is better described by reflections at higher 
+   $|\mathbf{q}|$ values. The location of R-pores \textit{is} important because we can 
+   use it to learn the number of monomer columns within each pore as we did in 
+   section~\ref{section:mon_per_pore}
+
   \subsubsection{The origin of R-spots}\label{section:rspots}
@@
   In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
-  configuration at 280K. Many force fields do not obtain the correct equilibrium structure at precisely the experimental temperature. Wang et al. highlighted the 
-  shortcoming of some of the most popular protein force field in predicting the temperature
-  dependence of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
-  our membrane system, simulated at 300K, is overly structured compared to the experimental structure at 300K.
-  We found that lowering the temperature better resolved the R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' temperature might indeed be too high, overstabilizing structure.
+  configuration at 280K. Many force fields do not obtain the correct equilibrium structure
+  at precisely the experimental temperature. Wang et al. highlighted the shortcoming of 
+  some of the most popular protein force field in predicting the temperature dependence 
+  of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
+  our membrane system, simulated at 300K, is overly structured compared to the experimental
+  structure at 300K. We found that lowering the temperature better resolved R-spots 
+  (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' temperature might 
+  indeed be too high, overstabilizing structure. 
 %  The relative intensity 
@@
 
-  Evidence 
-%MRS10: added
-from the simulations
-  strongly suggests that the R-spots signal is not a result of alkane
-  chain tilt. Previous literature has attributed the spots in this particular
-%MRS10: clarified that it was THIS exact data, and not similiar images. Correct if wrong.
-WAXS 
-%pattern 
-dataset
-as the product of tilted alkane chains~\cite{feng_scalable_2014}.
+  Evidence from the simulations strongly suggests that the R-spots signal is not a 
+  result of alkane chain tilt. Previous literature has attributed the spots in 
+  this particular WAXS dataset as the product of tilted alkane chains~\cite{feng_scalable_2014}.
   We measured the tilt angle of the alkane chains of the 280K system and showed
-  that it equilibrates to an average tilt angle of
-  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
-  used to explain R-spots. 
-  %MRS8: did you do a few different things here as sensitivity analysis to show that the finding was robust?  If so, putting some of that in would be useful.
-  %BJC7: make it clear that it is the 280K. Reference all configurations where tilt angles were calculated.
+  that it equilibrates to an average tilt angle of -2\degree~(Fig.~\ref{fig:tilt}),
+  far from the 37\degree~tilt angle previously used to explain R-spots.
 
@@
   %MRS10: rephrased.
-  The evidence strongly suggests that R-spot pattern occurs because tails pack together hexagonally. 
-  We plotted the center of masses of the 
-  first four tail atoms of each tail originating from each head group 
-  (Figure \ref{fig:centroids}). We measured the angle between each center of
-  mass and its nearest neighbor center of masses with respect to the $xy$ 
-  plane of the membrane. We see distinct peaks in the distribution of these 
-  angles located ca. $-60\degree$, $0\degree$, and $60\degree$ which is 
-  consistent with a hexagonally packed configuration 
+  The evidence strongly suggests that R-spot pattern occurs because tails pack 
+  together hexagonally. We plotted the center of masses of the first four tail 
+  atoms of each tail originating from each head group (Figure \ref{fig:centroids}).
+  We measured the angle between each center of mass and its nearest neighbor 
+  center of masses with respect to the $xy$ plane of the membrane. We see distinct
+  peaks in the distribution of these angles located ca. $-60\degree$, $0\degree$,
+  and $60\degree$ which is consistent with a hexagonally packed configuration 
   (Figure~\ref{fig:layered_tails}). 
   %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
+  %BJC10: I only addressed this because Matt wanted a more thorough characterization of tail order 
 This ordering dies off at the tail ends,
@@
 It could go either way (as I mention before, there's the issue of R-pi placement, too), but it should be consistent.
-  The experimentally measured R-$\pi$ is more intense relative to the experimental system. The difference in intensity
-  ranges from 3 times too high in the ordered parallel displaced system to 15 times too 
-  high in the ordered sandwiched configuration (Table~\ref{table:relative_inensities_300K}).
+  The simulated intensity of R-$\pi$ at 300K is more intense relative to the experimental 
+  system. The difference in intensity ranges from 3 times too high in the ordered parallel
+  displaced system to 15 times too high in the ordered sandwiched configuration 
+  (Table~\ref{table:relative_inensities_300K}).
   %MRS10: should specify this is in the 300 K simulations.
@@
   Additionally, we model each atom with a Gaussian sphere of electron density. 
-  The true electronic structure is likely much more complicated. 
-  %MRS10: modified
-  However, we can explore reasons for which differences in the simulation structure could changes the peak shapes to be in better agreement with experiment.
+  The true electronic structure is likely much more complicated. However, we can
+  explore reasons for which differences in the simulation structure could change
+  the peak shapes to be in better agreement with experiment.
 
@@
 
-%MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
-%BJC9: hahaha^
   \begin{figure}[!htb]
@@
   \subsubsection{Origin of R-double}\label{section:rdouble}
+
+  %BJC10: I think this belongs somewhere in this section.
+  The simulated XRD patterns of the parallel displaced configurations show additional
+  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
+  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
+  for the same reason as R-double. It is possible that parallel displaced monomers contribute
+  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.
 
@@
 
-  \subsection{Slow dynamics}
+  \subsection{Slow dynamics}\label{section:slow_dynamics}
 

### 2018-08-14 Ben_Manuscripts/structure_paper/Draft.tex
updated comments.

@@
   basins. We generated simulated patterns using the equilibrated portion of each 
-  simulation trajectory. The simulated diffraction patterns have some noise, especially
-  along the $q_z$ axis at $q_r$=0. There are two main reasons for this noise. First
-  is that we angle averaged the 3D structure factor (see section~\ref{method:xrd})
-  which inherently gives less data as $q_r$ approaches 0. Second, we hypothesize that 
-  the more important issue is that our simulations are not long enough to sample 
-  enough truly independent configurations within their respective metastable basins
-  (See section~\ref{section:slow_dynamics}). By sampling more uncorrelated equilibrium
-  configurations, we can suppress some of the noise (See section S-\ref{S-section:xrd_noise}
-  for a detailed example of this effect). The simulated patterns generated for all systems
+  simulation trajectory. 
+  %MRS11: probably want to say about about HOW they were generated (Could refer back to methods?)
+  %MRS11: my pass below.
+  There are two important factor to take into account when looking at differences between experimental XRD and simulated XRD.  First, the 
+  simulated diffraction patterns have some noise, especially
+  along the $q_z$ axis at $q_r$=0, which is where several of the more interesting features are located.
+  This is due to the angle averaging the 3D structure factor around the $q_z$-axis (see section~\ref{method:xrd}), meaning there are fewer samples as  $q_r$ approaches 0.
+The amount of samples to converge along the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}.
+  More importantly, are simulations do not appear to be long 
+  enough to sample 
+  truly independent configurations within their respective metastable basins
+  (See section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the results of the XRD. 
+  %MRS11: the fact that they are not within their metastable basis DOESN'T just affect the noise it affects everything else.
+If we had 100 times longer, it would reduce the noise along the z axis a lot, but the peaks would likely still be too intense, as we would have a lot of data long the z, but still be in the timescales that are too slow to reduce the peak intensity.
+Did a pass above.
+The simulated patterns generated for all systems
   studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
@@
   (Table~\ref{table:relative_inensities_300K}). Our methods for measuring the intensity of
-  each reflection are presented in section S-\ref{S-section:xrd_intensities}. We have
-  devoted individual subsections to explain each major reflection. We start with relatively 
-  uncomplicated analyses of experimentally-similar reflections:
+  each reflection are presented in section S-\ref{S-section:xrd_intensities}.
+
+  In the next few subsections, we have individually address each major reflection, and the similarities and differences between simulation and experiment. We start with relatively 
+  uncomplicated analyses of reflection that are very similar between experiment and simulation:
   %BJC10: Could make the following more descriptive.
 For example : "The location of R-alkanes", "The intensity of R-pores", "The origin of R-spots", "The shape and intensity of R-pi", "The origin of R-double".
+  %MRS11: that sounds good.
   \begin{itemize}

### 2018-08-16 Ben_Manuscripts/structure_paper/Draft.tex
Lots of draft updates

@@
 
+  \subsection{Simplified Systems}\label{method:simple_systems}
+
+  In order to gain a deeper understanding of discrepancies between the experimental and
+  and simulated R-$\pi$ reflection, we used a simplified baseline model where we 
+  represent each monomer as a single point scatterer located at the center of mass
+  of its head group. In order to make a system approximately similar to our equilibrated 
+  simulation geometries, we created 4 hexagonally packed pore regions spaced 42.5 \AA 
+  apart, each with 5 columns of scatterers spaced 4.4 \AA apart in the $z$-direction. We
+  built the system 4 times taller in the $z$-direction (80 scatterers per column) in order
+  to access higher $q_z$ resolution.
+
+  We gave the simplified models the same amount of disorder present in the atomistic
+  simulations. We observe two sources of disorder: thermal motion of atoms
+  and quenched disorder which is created by rapid structural rearrangement during 
+  early equilibration and is largely locked into place for the remainder of the 
+  simulation. We measured thermal disorder by calculating the standard deviation of 
+  the distribution of head group center of mass positions from their average positions.
+  We measured quenched disorder by calculating the standard deviation of the distribution
+  of head group center of masses from their idealized average positions. In the 
+  $z$-direction, we measured the deviation of the head group center of masses from an
+  equally spaced column of head groups. In the $xy$ plane, we calculated the standard 
+  deviation in radial position from the pore center and the angular deviation from 
+  equally spaced points surrounding the pore center. This method for calculating 
+  quenched order inherently includes thermal disorder.
+
+  We approximated interactions between particles by correlating the $z$-distance 
+  between points within each column of point scatterers. We placed points in each
+  column by drawing random samples from a multivariate normal distribution defined
+  by the mean positions of an equally spaced column of points. We gave the 
+  distribution at each point along the column the same standard deviation, 
+  $\sigma_z$ and we defined a covariance matrix such that the covariance, $v$, of
+  the distance, $d$, between scatterers decays exponentially from $v$ according
+  to the equation $ve^{-d/L}$, where $L$ is the correlation length. We used the
+  experimental correlation length of 9.0 $\AA$.
+
+  We calculated averaged R-$\pi$ profiles by simulating the diffraction pattern
+  of trajectories consisting of 1000 independent simple system configurations 
+  generated with point scatterer placement based on the quenched order seen in
+  atomistic simulations. The quenched disorder is greater in  magnitude than thermal 
+  disorder (See Table~\ref{table:quenched_disorder} in section~\ref{section:rpi})
+  and inherently includes thermal disorder due to the way we calculate it.
+  This method assumes that the timescales for large scale rearrangements of the
+  system are much longer than what we can feasibly simulate.
+
   \subsection{Cross-linking}
@@
   diffraction patterns produced from equilibrated MD trajectories and comparing them
-  to experiment. We tested systems built with 5 columns per pore in the parallel 
-  displaced and sandwiched configurations at 300 K in the ordered and disordered
-  basins. We generated simulated patterns using the equilibrated portion of each 
-  simulation trajectory. 
-  %MRS11: probably want to say about about HOW they were generated (Could refer back to methods?)
-  %MRS11: my pass below.
-  There are two important factor to take into account when looking at differences between experimental XRD and simulated XRD.  First, the 
-  simulated diffraction patterns have some noise, especially
-  along the $q_z$ axis at $q_r$=0, which is where several of the more interesting features are located.
-  This is due to the angle averaging the 3D structure factor around the $q_z$-axis (see section~\ref{method:xrd}), meaning there are fewer samples as  $q_r$ approaches 0.
-The amount of samples to converge along the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}.
-  More importantly, are simulations do not appear to be long 
-  enough to sample 
-  truly independent configurations within their respective metastable basins
-  (See section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the results of the XRD. 
+  to experiment (see section~\ref{method:xrd}). We tested systems built with 5 columns
+  per pore in the parallel displaced and sandwiched configurations at 300 K in the 
+  ordered and disordered basins. We generated simulated patterns using the equilibrated
+  portion of each simulation trajectory. There are two important factors to take into
+  account when looking at differences between experimental XRD and simulated XRD. First,
+  the simulated diffraction patterns have some noise, especially along the $q_z$ axis 
+  at $q_r$=0, which is where several of the more interesting features are located. This
+  is due to the angle averaging of the 3D structure factor around the $q_z$-axis, meaning
+  there are fewer samples as  $q_r$ approaches 0. The amount of samples to converge along
+  the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}. 
+  More importantly, our simulations do not appear to be long enough to sample truly 
+  independent configurations within their respective metastable basins (See 
+  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the
+  results of the XRD. The simulated patterns generated for all systems studied are shown
+  and compared to experiment in Figure~\ref{fig:XRDsim}.
+
   %MRS11: the fact that they are not within their metastable basis DOESN'T just affect the noise it affects everything else.
@@
 Did a pass above.
-The simulated patterns generated for all systems
-  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
 
@@
 
-  In the next few subsections, we have individually address each major reflection, and the similarities and differences between simulation and experiment. We start with relatively 
-  uncomplicated analyses of reflection that are very similar between experiment and simulation:
-  %BJC10: Could make the following more descriptive.
-For example : "The location of R-alkanes", "The intensity of R-pores", "The origin of R-spots", "The shape and intensity of R-pi", "The origin of R-double".
-  %MRS11: that sounds good.
+  In the next few subsections, we individually address each major reflection, and the
+  similarities and differences between simulation and experiment. We start with relatively 
+  uncomplicated analyses of reflections that are very similar between experiment and simulation:
   \begin{itemize}
-  	\item R-alkanes (section~\ref{section:ralkanes})
-  	\item R-pores (section~\ref{section:rpores})
+  	\item The location of R-alkanes (section~\ref{section:ralkanes})
+  	\item The intensity of R-pores (section~\ref{section:rpores})
   \end{itemize}
@@
   \begin{itemize}
-  	\item R-spots (section~\ref{section:rspots})
-  	\item R-$\pi$ (section~\ref{section:rpi})
-  	\item R-double (section~\ref{section:rdouble})
+  	\item The origin of R-spots (section~\ref{section:rspots})
+  	\item The position, shape and intensity of R-$\pi$ (section~\ref{section:rpi})
+  	\item The origin of R-double (section~\ref{section:rdouble})
   \end{itemize}
@@
   R-pores    & 12.3       & 49.5       & 54.0      & 50.8       & 53.4               \\
-  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
+  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
   R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
@@
 
-  \subsubsection{R-alkanes}\label{section:ralkanes}
+  \subsubsection{The location of R-alkanes}\label{section:ralkanes}
+
+  We normalized the experimental and simulated diffraction patterns so that the average
+  intensity within R-alkanes is equal to 1 because we believe that R-alkanes is the
+  experimental feature most likely to be reproduced by our simulations.
+  %BJC11: could add some support of this statement - perhaps a reference to the original
+  % GAFF forcefield paper? Need to actually check it though.
 
   R-alkanes appears close to its expected location. In all cases, the maximum intensity
-  of R-alkanes appears at a $|\mathbf{q}|$ value slightly higher than experiment. 
+  of R-alkanes appears at a $|\mathbf{q}|$ value only slightly higher than experiment. 
   We expect that the exact location of R-alkanes will not be perfect in our simulations
@@
   system size, however we are satisfied with the packing distances shown by our simulations.
-  %BJC10: I could integrate a 3D correlation function to get a better value
-
-  We believe that R-alkanes is the experimental feature most likely to be reproduced by
-  our simulations. For this reason we normalized the experimental and simulated diffraction
-  patterns so that the average intensity within the R-alkanes is equal to 1.
-
-  \subsubsection{R-pores}\label{section:rpores}
-
-   R-pores is about 4 times more intense than experiment in all simulated systems. 
-   %BJC10: trying to come up with a good explanation.
+  %BJC11: I could integrate a 3D correlation function to get a better value
+
+  \subsubsection{The location and intensity of R-pores}\label{section:rpores}
+
+  R-pores is about 4 times more intense than experiment in all simulated systems. We
+  hypothesize that this is primarily due to the relatively perfect infinite hexagonal
+  array of pores in the simulated systems. In the real system, periodicity of the 
+  hexagonal array is disrupted by misalignment of the crystalline domains and the
+  pore-to-pore distances fluctuate more over long time scales. 
+  % BJC11: Using simple systems, I can show that more highly fluctutating pore-to-pore
+  % distances will decrease the intensity of R-pores. I don't think its worth getting
+  % into in the main text. It's the same idea as how increased z-noise decreases the intensity of R-pi
+  % BJC11: I also think that domain misalignment in the z-direction contributes. If you
+  % imagine a hexagonal array of pores aligned along the z-axis, then rotate that axis
+  % so it has an x and y component, then there will be constructive interference perpendicular
+  % to that axis at non-zero qz values. That is why R-pores is arced. It's a different
+  % type of broadening than R-pi - I think
+  % BJC11: I don't think a deep dive into this is worth it. It's dependent on things
+  % unrelated to the actual pore structure.
 
   We are not concerned with exactly reproducing the intensity of R-pores since it is a 
-   product of long distance correlation between pores. We are primarily concerned with
+  product of long distance correlations between pores. We are primarily concerned with
   the structure within pores which is better described by reflections at higher 
-   $|\mathbf{q}|$ values. The location of R-pores \textit{is} important because we can 
-   use it to learn the number of monomer columns within each pore as we did in 
-   section~\ref{section:mon_per_pore}
+  $|\mathbf{q}|$ values.
+
+  The location of the leading peak of R-pores is geometrically related to the average 
+  distance between pores. However, there is uncertainty in its exact location because
+  the Fourier bin size is so large. We can measure the average distance between columns
+  with more precision in real space (See Section~\ref{method:pore_spacing}). We showed
+  that we achieve experimentally consistent pore spacings in our simulations in 
+  Section~\ref{section:section:mon_per_pore}.
 
   \subsubsection{The origin of R-spots}\label{section:rspots}
-%MRS10: I rephrased the below, check the diffs.
+
+  The intensity of R-spots is close to experiment when generated from any of our
+  simulated systems. The appearance of R-spots is inconspicuous in most cases so we
+  assumed that the location of R-spots, in terms of $|\mathbf{q}|$ would coincide with
+  that of R-alkanes, and that it's $q_z$ location should be roughly in line with 
+  R-double (half the $q_z$ location of R-$\pi$) as it appears in the experimental pattern.
+  We measured the intensity of R-spots by radially integrating the simulated
+  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$ (between
+  4 and 4.5 $\AA$ in real space) and then locating and recording the intensity of the 
+  appropriate peaks in the resulting distribution.
+
+  R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
+  Previous literature has attributed the spots in this particular WAXS dataset as 
+  the product of tilted alkane chains~\cite{feng_scalable_2014}. Here we refute 
+  that explanation and show that the tails do not tilt, but rather pack in a 
+  hexagonal array.
+
   In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
@@
   of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
-  our membrane system, simulated at 300K, is overly structured compared to the experimental
-  structure at 300K. We found that lowering the temperature better resolved R-spots 
-  (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' temperature might 
-  indeed be too high, overstabilizing structure. 
-%  The relative intensity 
-%  of R-spots in this system is slightly higher than experiment (1.5 vs. 1.3)
-
-%  We observe an increase in the intensity of R-spots when we simulate systems at 280K. R-spots
-%  is most intense in the ordered basin sandwiched configuration (Figure~\ref{fig:sandwiched280K}). 
-%  The relative intensity of R-spots is slightly higher than in experiment (1.5 vs. 1.3). R-double 
-%  is still not present. We will use the system simulated at 280K to more thoroughly explore the 
-%  origin of R-spots.
+  our membrane system, simulated at 300K, is under-structured in the tail region compared
+  to the experimental structure at 300K. We found that lowering the temperature better 
+  resolved R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' 
+  temperature might indeed be too high, understabilizing structure.
 
   Evidence from the simulations strongly suggests that the R-spots signal is not a 
-  result of alkane chain tilt. Previous literature has attributed the spots in 
-  this particular WAXS dataset as the product of tilted alkane chains~\cite{feng_scalable_2014}.
-  We measured the tilt angle of the alkane chains of the 280K system and showed
-  that it equilibrates to an average tilt angle of -2\degree~(Fig.~\ref{fig:tilt}),
-  far from the 37\degree~tilt angle previously used to explain R-spots.
-
-  %To understand the most likely origin of R-spots, we determined which atoms
-  %gave rise to the feature. 
-  Although the monomer tails do not tilt, R-spots still originates from the 
+  result of alkane chain tilt. We measured the tilt angle of the alkane chains of
+  the 280K system and showed that it equilibrates to an average tilt angle of
+  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
+  used to explain R-spots.
+
+  Although the monomer tails do not tilt, R-spots still originates from 
   them. By removing all non-tail atoms from the trajectory and simulating a
@@
 
-  %BJC9: I think Matt gets confused here. I put a more detailed explanation in 
-  % the supplemental information. Do you think that's enough, or should I add
-  % to this figure?
-  %MRS10: rephrased.
-  The evidence strongly suggests that R-spot pattern occurs because tails pack 
+  %BJC11: need to rephrase -- "strongly suggests" used two paragraphs prior
+  The evidence strongly suggests that R-spots occurs because tails pack 
   together hexagonally. We plotted the center of masses of the first four tail 
-  atoms of each tail originating from each head group (Figure \ref{fig:centroids}).
-  We measured the angle between each center of mass and its nearest neighbor 
-  center of masses with respect to the $xy$ plane of the membrane. We see distinct
-  peaks in the distribution of these angles located ca. $-60\degree$, $0\degree$,
-  and $60\degree$ which is consistent with a hexagonally packed configuration 
-  (Figure~\ref{fig:layered_tails}). 
+  atoms of all tails (Figure \ref{fig:centroids}). We measured the angle between
+  each center of mass and its nearest neighbor center of masses with respect to
+  the $xy$ plane of the membrane. We see distinct peaks in the distribution of
+  these angles located ca. $-60\degree$, $0\degree$, and $60\degree$ which is
+  consistent with a hexagonally packed configuration (Figure~\ref{fig:layered_tails}). 
   %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
   %BJC10: I only addressed this because Matt wanted a more thorough characterization of tail order 
-This ordering dies off at the tail ends,
-  where there is more space to fill causing them to pack nearly isotropically.
-  See Section~S-\ref{S-tail_packing} for a more detailed explanation of the 
-  calculation and packing distributions generated from different sections of
-  the tails.
-
-  The peaks in the nearest neighbor angle distribution due to the hexagonal packing are consistent with the
-  location of R-spots. The 2D Fourier transform of a simple hexagonal array 
-  constructed based on the peak angles in Figure~\ref{fig:layered_tails}
-  shows reflections in the same locations as R-spots, in addition to vertical 
-  stacking reflections along the $q_z$ axis that would intersect with R-$\pi$
-  (Figure~\ref{fig:hexagonal_ft}).
-
-% BJC5: omit for now
-%  The evidence supports the hypothesis that alkane chain tails pack in a
-%  hexagonal array. Groups of three tails associated with each monomer prefer to
-%  sit between tails of vertically stacked monomers rather than stacking directly
-%  on top of them (Figure~\ref{fig:hex_tails}). This type of packing has been seen
-%  before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.
-
-% BJC6 : added better justification to beginning of section
-%  %MRS7: couple -> ``two main''?
-%%MRS7: what is the purpose of this paragraph?  I think most people would know why a lower T simulation would be more ordered (though the degree is not known).
-%  There are two reasons why we see stronger ordered chain packing at 280 K compared to
-%  experimental conditions of 300 K.
-%  \begin{enumerate}
-%  		\item The difference between 280 K and 300 K is relatively small. Our forcefield parameters
-%  		may not correctly model the behavior of the tails at 300 K (citation?).
-%                % look for papers on protein folding temperature dependence: see Lee-Ping Wang's AMBER-15fb paper
-%  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
-%  		If the head groups packed 3.7 \AA~apart, the tails would be more confined and forced
-%  		to pack between vertically adjacent monomer tails. In our case, the tail region is
-%  		less dense than experiment which gives the tails freedom to organize in a more
-%  		entropically favored disordered state. 
-%  \end{enumerate}
+  This ordering dies off at the tail ends, where there is more space to fill 
+  causing them to pack nearly isotropically. See Section~S-\ref{S-tail_packing}
+  for a more detailed explanation of the calculation and packing distributions
+  generated from different sections of the tails.
+
+  The peaks in the nearest neighbor angle distribution due to the hexagonal 
+  packing are consistent with the location of R-spots. The 2D Fourier transform
+  of a simple hexagonal array constructed based on the peak angles in 
+  Figure~\ref{fig:layered_tails} shows reflections in the same locations as R-spots,
+  in addition to vertical stacking reflections along the $q_z$ axis that would 
+  intersect with R-$\pi$ (Figure~\ref{fig:hexagonal_ft}).
 
@@
 
-  \subsubsection{Discrepancies between experimental and simulated R-$\pi$}\label{section:rpi}
-  %MRS10: in the list of questions above, you just talk about intensity, but this title talks about more discrepnacies.
-It could go either way (as I mention before, there's the issue of R-pi placement, too), but it should be consistent.
-  The simulated intensity of R-$\pi$ at 300K is more intense relative to the experimental 
-  system. The difference in intensity ranges from 3 times too high in the ordered parallel
-  displaced system to 15 times too high in the ordered sandwiched configuration 
-  (Table~\ref{table:relative_inensities_300K}).
-  %MRS10: should specify this is in the 300 K simulations.
-
-  The peak shape of the $q_r$ cross-section of R-$\pi$ in the simulated XRD is qualitatively different
-  from experiment (Figures~\ref{fig:exp_rsection_fit} and~\ref{fig:sim_rsection_fit}).
-  We use simulated XRD generated from the ordered parallel displaced configuration
-  as an example in Figure~\ref{fig:rpi_exp_comparison}. The $q_z$ cross-section 
-  fits a Lorentzian profile relatively well, although its full width at half maximum
-  (FWHM) is 48\% broader than the experimental cross-section 
-  (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). We attempted
-  to fit a Lorentzian profile to the $q_r$ cross-section and although the FWHM agrees
-  with experiment within error, the fit is not optimal due to the three sharp peaks
-  that appear near $q_r$ = 0.
-
-  An exact quantitative comparison between experiment and simulation is not feasible for several reasons. 
-  Experimental peaks broaden due to effects that we can not easily simulate such
-  as finite size crystalline domains and instrumental resolution. In our simulated
-  XRD patterns, the system size imposes limitations on the resolution, which makes
-  it difficult to reliably fit peaks. This is especially problematic when comparing
-  the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental FWHM 
-  (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
+  \subsubsection{The position, shape and intensity of R-$\pi$}\label{section:rpi}
+
+  The position, shape and intensity of R-$\pi$, generated from simulations at 300K, are 
+  qualitatively and quantitatively different than experiment. The reflections appear
+  at lower $q_z$ values, they are more intense and the shape of its cross-sections, 
+  especially in the $q_r$ direction are different relative to the experimental system
+  (See Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the simulated
+  XRD generated from the ordered parallel displaced configuration as an example). In 
+  this section, we explore the various contributions to these discrepancies, and use what
+  we've learned to speculate on improvements to our initial configurations and simulation
+  procedures.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
+  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
+  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
+  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
+  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
+  \end{subfigure}
+  \caption{
+  The maximum intensity of R-$\pi$ generated from simulations of the ordered
+  parallel displaced configuration is 3 times larger than experiment. The $q_r$
+  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between 
+  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
+  the FWHM of the simulated pattern agrees with experiment within error, however
+  the fit to the simulated data is obscured by the three sharp peaks which appear
+  near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
+  qualitatively similar. Each fits a Lorentzian profile well, however the FWHM
+  of the simulated cross-section (d) is 48\% larger than the experimental 
+  cross-section. Additionally, peak of the simulated $q_z$ cross-section is 
+  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
+  \end{figure}
+
+%  The difference in intensity ranges from 3 times too high in the ordered parallel
+%  displaced system to 15 times too high in the ordered sandwiched configuration 
+%  (Table~\ref{table:relative_inensities_300K}).
+
+  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment because
+  monomers in the simulated system stack further apart than those in the experimental
+  system (Table~\ref{table:correlation_length}). We calculated $z$-direction pair distribution
+  functions, $g(z)$, as described in Section~\ref{section:correlation_length}.
+  %BJC11: Below is in methods but might be worth restating here? 
+%  based on the center of mass of each monomer head group. In order
+%  to calculate $g(z)$, we averaged all $z$-slices of the 3D pair distribution function, $g(x, y, z)$, 
+%  (Equation~\ref{eqn:correlation}) within
+%  2.1 \AA~of $g(0, 0, z)$. In this way we are measuring correlation between head 
+%  groups within the same column. 
+  The resulting distributions are generally characterized
+  by decaying oscillatory behavior where the average distance between peaks corresponds
+  to the average distance between stacked monomer head groups (Figure~\ref{fig:correlation}).
+  We calculated this equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between
+  monomers using Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked
+  monomers is greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
+  basins at the high part of that range, 0.2 and 0.3 \AA~more distant. This behavior is
+  not surprising since GAFF models atoms as point charges and  % BJC11: need reference
+  does not appropriately model the aromatic $\pi-\pi$ interactions which would make it
+  more energetically favorable for the monomers to stack closer together. Additionally, 
+  it is possible that the tails prevent close stacking of monomer head groups and we do
+  not achieve the timescales necessary for them to rearrange into a necessarily more
+  tightly packed configuration. We equilibrated the system at 500K then annealed it to 300K
+  in an attempt to coerce the tails into a more tightly packed configuration, however 
+  we saw no improvement over our 300K models. See section S-TBD for details.
+
+  The system size, in the $z$-direction, does not significantly alter $g(z)$. 
+  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
+  system may be necessary to fully capture the correlation function. We 
+  equilibrated a sandwiched system with twice as many monomers per column 
+  so that the system size doubled in the $z$-direction. The correlation length 
+  increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. Visually, the
+  correlation functions are nearly identical and oscillatory behavior persists
+  throughout $g(z)$ in both cases (See Figure~S-\ref{S-fig:z_correlation_overlay}).
+
+  The broadening of the $q_z$ cross-section of R-$\pi$ is related to $z$-directional
+  correlation between scatters within monomer columns. One can determine the correlation length as the
+  inverse of the full width at half maximum (FWHM) of the $q_z$ cross-section of R-$\pi$.
+  Using this technique, we calculated the correlation length of the experimental system
+  to be 9.0 \AA. As scatterers become less correlated, we expect that R-$\pi$ will broaden.
+
+  The correlation lengths of vertically stacked scatterers in our atomistic simulations
+  are in reasonable agreement with experiment. Since it is not feasible for us to
+  simulate membranes with much taller columns, for increased $q_z$ resolution of our
+  simulated XRD patterns, and because the simulated peak shape is convoluted by the
+  extremely intense maximum of R-$\pi$, we measured correlation length by fitting
+  Equation~\ref{eqn:decaying_exponential} to the peaks of $g(z)$. The correlation 
+  length of the parallel displaced, ordered basin system shows the closest agreement
+  with experiment (Table~\ref{table:correlation_length}). 
+  %BJC11: below might confuse the reader
+%  Note that its correlation length
+%  ($L$ = 14.5 \AA) is larger than what we would expect by inverting the FWHM of the $q_z$
+%  cross-section of R-$\pi$ shown in Figure~\ref{fig:sim_zsection_fit} ($L$ = 1 / 0.163 
+%  = 6.1 \AA). The reason is likely a combination of artificial broadening caused by the
+%  overlap of R-alkanes and R-$\pi$ as well as uncertainty in the fit due to low simulated
+%  XRD resolution.
+   We could not extract a reliable correlation
+  length from the disordered parallel displaced configuration since the peaks do not show
+  clear patterns that can easily be fit to an exponential decay. The correlation length
+  of both sandwiched systems are relatively low because the height of the first peak of 
+  $g(z)$ is so high.
+
+  %BJC11: trying to figure out how to communicate distance correlation
+  % wikipedia's explanation of distance correlation makes it seem like we are using it right:https://en.wikipedia.org/wiki/Distance_correlation
+  % could say "distance covariance"
+  Overall, we believe our simulations exhibit a realistic amount of distance correlation
+  between head groups within each column. The difference in the FWHM of the $q_z$ 
+  cross-section of R-$\pi$ between experiment and simulation is less than one bin size
+  (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). The more 
+  prevailing difference between the two cross-sections is their maximum intensity which
+  we study in more detail below.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
+  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_offset.png}
+  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
+  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
+  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
+  \end{subfigure}  
+  %MRS10: should say something here about whether this is consistent or not with experiement (and why/why not)
+  %MRS10: maybe include correlation lengths as well calculated from these, and compare to experiment?
+I know it's in the table as well, but seems missing here.
+1D correlation functions are given, but not how that data proves central points.
+  \caption{1D correlation functions of the center of masses of aromatic head
+	  groups, $g(z)$, show decaying oscillatory behavior. We calculated the
+	  correlation length by fitting a decaying exponential function
+	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
+	  correlation length is longer for ordered basin systems
+	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
+	  correlation length for (d) because there are no clear peaks. We assume that its
+	  correlation is less than the vertical distance between monomers.}\label{fig:correlation}
+  \end{figure}
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cccc}
+  \toprule
+  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
+  \midrule
+  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
+  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
+  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
+  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
+  Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
+  \bottomrule
+  \end{tabular}
+  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
+  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
+  \label{table:correlation_length}
+  \end{table}
+
+  In addition to the maximum intensity of R-$\pi$ being too high, the shape
+  of its $q_r$ cross-section in the simulated XRD is qualitatively different
+  from experiment (Figures~\ref{fig:exp_rsection_fit}
+  and~\ref{fig:sim_rsection_fit}). We attempted to fit a Lorentzian profile to 
+  the $q_r$ cross-section and although the FWHM agrees with experiment within
+  error, the fit is not optimal due to the three sharp peaks that appear near
+  $q_r$ = 0.
+
+  An exact quantitative comparison between the intensity and FWHM of the experimental
+  and simulated cross-sections of R-$\pi$ is not feasible
+  for several reasons. Experimental peaks broaden due to effects that we can not 
+  easily simulate such as finite size crystalline domains and instrumental resolution.
+  In our simulated XRD patterns, the system size imposes limitations on the resolution,
+  which makes it difficult to reliably fit peaks. This is especially problematic when
+  comparing the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental 
+  FWHM (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
   Additionally, we model each atom with a Gaussian sphere of electron density. 
@@
   explore reasons for which differences in the simulation structure could change
-  the peak shapes to be in better agreement with experiment.
+  the peak shapes and intensities to be in better agreement with experiment.
 
@@
 
-  %MRS9: State explicitly in what way the discrepancy would increase, i.e.
-experimental FWHM are broadened by other source (doppler pressure, insttrument broadening) that do no affect the simulated spectra, the experimental spectra may be even narrower than spectra generated from simulations are.
-  %MRS9: one question, do any of the approximations used in the simulation actually lead to broadening that would not be in experiment (gaussian scatterers, etc.
-Also, (semi-related) do Gaussian scatters lead to Gaussian peaks?
-Fourier transforms of Gaussians are Gaussians)
-  % BJC8: Can add more detail about different types of broadening - instrument / finite resolution broadening (for
-  % experimental case), doppler (gaussian shaped) and pressure broadening (Lorentzian shaped)
-  % See: https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-7
-  %MRS 9: it is a little problematic to use two different types of fit, as the FWHM is a little different for each of then.
-Would lead to slight discrepancies from that.
-FWHM is a natural scale parameter for Lorenzians, but not really for Gaussian.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
-  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
-  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
-  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
-  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
-  \end{subfigure}
-  \caption{
-%  There are clear qualitative differences between the experimental WAXS pattern 
-%  ((a) and (c)) and the simulated XRD pattern resulting from simulations 
-%  of the ordered parallel displaced configuration ((b) and (d)). 
-    %MRS10: don't make the thesis what was done, but what the reader should know. 
-  We compared the experimental WAXS pattern ((a) and (c)) to the simulated XRD
-  pattern resulting from simulations of the ordered parallel displaced 
-  configuration ((b) and (d)). The $q_r$ cross-section of R-$\pi$ ((a) and (b))
-  is qualitatively different between experiment (a) and simulation (b). We fit
-  Lorentzian profiles to each peak and the FWHM of the simulated pattern agrees
-  with experiment within error, however the fit to the simulated data is 
-  obscured by the three sharp peaks which appear near $q_r$ = 0. The $q_z$ 
-  cross-sections of R-$\pi$ ((c) and (d)) are qualitatively similar. Each fits
-  a Lorentzian profile well, however the FWHM of the simulated cross-section (d)
-  is 48\% larger than the experimental cross-section.}\label{fig:rpi_exp_comparison}
-  \end{figure}
-
-  We have identified a number of potential ways that simulation conditions,
-  forcefield and initial configurations could affect the intensity and shape of
-  R-$\pi$, and assess each using a simplified model of the pore. Our simplified model 
-  represents each monomer head group as a single point and places them in either
-  a parallel displaced or sandwiched configuration. We chose to explore the 
-  influence of thermal noise in each dimension, the effect of $z$-direction 
-  distance correlations between scatterers within columns, as well as correlation
-  between columns since these are the variables we believe have the largest 
-  influence on peak shape and intensity.
-
-  %MRS10: somewhere in here, we need to address whether quenched and static disorder are 
-  % the same experimentally. If not the same, then it's glassy, if they are the same, then 
-  % we are making the assumption that the the timescales of motion of that noice are > 1 microsecond but < 1 second.
-  We created a simplified baseline model using the same amount of
-  disorder present in our atomistic simulations. There are two sources of
-  disorder to consider: thermal motion of atoms and quenched disorder which is
-  created by rapid structural rearrangement during early equilibration and 
-  is largely locked into place for the remainder of the simulation. The latter
-  has important implications 
-  %MRS10: which are the important implications?
-for the reproducibility of this work since both 
-  initial configuration and initial velocity randomization can lead to 
-  different quenched configurations. We measured thermal disorder by
-  calculating the standard deviation of the distribution of head group center 
-  of mass positions from their average positions. We measured quenched 
-  disorder by calculating the standard deviation of the distribution of head
-  group center of masses from their idealized average positions. In the 
-  $z$-direction, we measured the deviation of the head group center of masses
-  from an equally spaced column of head groups. In the $xy$ plane, we 
-  calculated the deviation in radial position from the pore center and the
-  angular deviation from equally spaced points surrounding the pore center.
-  This method for calculating quenched order inherently includes thermal 
-  disorder. The values measured for each system and type of disorder are given
-  in Table~\ref{table:quenched_disorder}.
-
-  %MRS10: this is more of a methodological thesis than is ideal. Can you make it more about what we are learning, or at least what was done and the reasoning?
-  The expected maximum intensity of R-$\pi$ can be calculated from a single
-  trajectory of uncorrelated configurations rather than from the average of 
-  multiple trajectories of correlated frames. Theoretically, in order to
-  mimic the simulated system, we should build an initial configuration which 
-  has the same amount of quenched disorder as our simulations and then create
-  a trajectory to which we add thermal noise to each subsequent frame. In this
-  scenario, the positions of each scatterer will not change in a way that 
-  significantly affects the intensity of R-$\pi$ since most of its character 
-  is defined by the far more disordered initial configuration. To uncover the
-  expected intensity of R-$\pi$, we would need to average over many such 
-  trajectories. To bypass this expensive calculation, we instead calculate the
-  R-$\pi$ intensity from a trajectory consisting of many independent initial 
-  configurations. This simulates the long time scales over which we expect 
-  columns to sample many configurational states. %We use the latter method 
-  %for the remainder of this section since we can extract the trends we 
-  %need using a single trajectory at a fraction of the computational cost.
-
-  %MRS10: again, more of a methodolgical thesis.  Will not be clear to the reader what they are 
-  % expecting to learn, which is the difference in the simulation that could explain the differences in the spectra.
-  % I'm thinking some of this should be in the supporting info.  Maybe not, if key enough, but it should still be in support of the conclusion. 
-  When we simulated the diffraction pattern of a parallel displaced simple
-  system trajectory of 1000 independent configurations, the
-  $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
-  this simple system, and all to follow, 4 times taller in the $z$-direction in
-  order to access higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation}
-  and~\ref{fig:sf_qz_correlation} shows the $q_y$ and $q_z$ cross-sections of
-  R-$\pi$ generated by simulating the structure factor of the trajectory. The
-  distance between peaks in the $q_y$ cross-section is equivalent to the distance
-  between pores in real space.
+% BJC11: paragraph seems unnecessary
+%  We have identified a number of potential ways that simulation conditions,
+%  forcefield and initial configurations could affect the intensity and shape of
+%  R-$\pi$, and we assessed each using a simplified model of the pores. Our simplified model 
+%  represents each monomer head group as single point scatterers and places them in either
+%  a parallel displaced or sandwiched configuration. We chose to explore the 
+%  influence of thermal noise in each dimension, the effect of $z$-direction 
+%  distance correlations between scatterers within columns, as well as correlation
+%  between columns since these are the variables we believe have the largest 
+%  influence on peak shape and intensity.
+
+  We studied the shape and intensity of R-$\pi$ by setting up simplified systems
+  where we represent monomer head groups as point scatterers, as described in 
+  Section~\ref{method:simple_systems}. The amount of quenched and thermal disorder
+  present in the atomistic system, which we applied to the simplified systems, are
+  given in Table~\ref{table:quenched_disorder}. The magnitude of quenched disorder
+  is greater than thermal disorder.
 
@@
 
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
-  \caption{}\label{fig:sf_qy_nocorrelation}
-  \end{subfigure}
-  \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
-  \caption{}\label{fig:sf_qy_correlation}
-  \end{subfigure} 
-  \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
-  \caption{}\label{fig:sf_qz_correlation}
-  \end{subfigure}   
-  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
-  points meant to represent monomer head groups. We added a similar amount of noise to 
-  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
-  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
-  peaks. (b) When we correlate the distance between points within each column, the 
-  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
-  intensity between the center and outer peaks. (c) Correlation of the distance between
-  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
-  \end{figure}
-
-  The distances between scatterers within each column are correlated with each
-  other. In the simplified system described above, we added Gaussian noise to
-  the mean positions of an equally spaced column of points. This ignores any
-  interaction head groups might have with each other. To remedy this, we drew
-  random samples from a multivariate normal distribution defined by the mean
-  positions of an equally spaced column of points. We gave the distribution at
-  each point along the column the same standard deviation, $\sigma_z$, shown in
-  Table~\ref{table:quenched_disorder}. We defined a covariance matrix such
-  that the covariance, $v$, of the distance, $d$, between scatterers decays
-  exponentially from $v$ according to the equation $ve^{-d/L}$, where $L$ is the
-  correlation length. Experimentally, the correlation length can be estimated as
-  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$. Accordingly,
-  the correlation length of the experimental system is $\geq$ 9 $\AA$. The value
-  may be larger since the peak is likely broadened. We simulated the structure
-  factor of a simple system built as described above with a correlation length of
-  30 $\AA$. We chose 30 $\AA$ in order to exaggerate the effect of correlation
-  length for visual purposes. Subsequent structure factor calculations are all
-  done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section
-  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$
-  cross-section (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in
-  experiment. Additionally, there is a near 20\% increase in the maximum
-  intensity of R-$\pi$ when the distances between scatterers are correlated.
+  %MRS10: somewhere in here, we need to address whether thermal and quenched disorder are 
+  % the same experimentally. If not the same, then it's glassy, if they are the same, then 
+  % we are making the assumption that the the timescales of motion of that noice are > 1 microsecond but < 1 second.  
+  %BJC11: most of this section moved to methods.
+%  We can study the shape and intensity of R-$\pi$ using a simplified baseline model
+%  which has the same amount of disorder present in our atomistic simulations. For these
+%  models, we represent each monomer as single point scatterers located at the center of mass of
+%  each monomer head group, and place them in a configuration spatially similar to those
+%  seen in our simulations. We made them 4 times taller in the $z$-direction in order to access
+%  higher $q_z$ resolution. When placing points, there are two sources of disorder to consider: 
+%  thermal motion of atoms and quenched disorder which is created by rapid structural 
+%  rearrangement during early equilibration and is largely locked into place for the remainder
+%  of the simulation. We measured thermal disorder by calculating the standard deviation of 
+%  the distribution of head group center of mass positions from their average positions. We 
+%  measured quenched disorder by calculating the standard deviation of the distribution of head
+%  group center of masses from their idealized average positions. In the $z$-direction, we
+%  measured the deviation of the head group center of masses from an equally spaced column
+%  of head groups. In the $xy$ plane, we calculated the standard deviation in radial position
+%  from the pore center and the angular deviation from equally spaced points surrounding 
+%  the pore center. This method for calculating quenched order inherently includes thermal 
+%  disorder. The values measured for each system and type of disorder are given
+%  in Table~\ref{table:quenched_disorder}. The magnitude of quenched disorder is greater than
+%  thermal disorder.
+
+  %BJC11: moved a variation of this to methods
+%  To avoid any dependence on initial configuration, we calculated the average R-$\pi$
+%  profile using simple system trajectories of 1000 independent configurations. We
+%  determined the amount of disorder to add to each independent configuration using
+%  the values for quenched disorder given in Table~\ref{table:quenched_disorder}.
+
+  %MRS10: this is more of a methodological thesis than is ideal. Can you make it more about what we are learning, or at least what was done and the reasoning?  
+%  The expected maximum intensity of R-$\pi$ can be calculated from a single
+%  trajectory of uncorrelated configurations rather than from the average of 
+%  multiple trajectories of correlated frames. Theoretically, in order to
+%  mimic the simulated system, we should build an initial configuration which 
+%  has the same amount of quenched disorder as our simulations and then create
+%  a trajectory to which we add thermal noise to each subsequent frame. In this
+%  scenario, the positions of each scatterer will not change in a way that 
+%  significantly affects the intensity of R-$\pi$ since most of its character 
+%  is defined by the far more disordered initial configuration. To uncover the
+%  expected intensity of R-$\pi$, we would need to average over many such 
+%  trajectories. To bypass this expensive calculation, we instead calculate the
+%  R-$\pi$ intensity from a trajectory consisting of many independent initial 
+%  configurations. This simulates the long time scales over which we expect 
+%  columns to sample many configurational states. %We use the latter method 
+%  %for the remainder of this section since we can extract the trends we 
+%  %need using a single trajectory at a fraction of the computational cost.
+
+% BJC11: I eliminated this figure and the discussion of distance correlation between
+% scatterers since the only real issue with the qz cross-section is the intensity. 
+% I explain how we create correlated distances in the methods. We weren't really 
+% showing anything new since correlation length equal 1 / FWHM_qz
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.3\textwidth}
+%  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
+%  \caption{}\label{fig:sf_qy_nocorrelation}
+%  \end{subfigure}
+%  \begin{subfigure}{0.3\textwidth}
+%  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
+%  \caption{}\label{fig:sf_qy_correlation}
+%  \end{subfigure} 
+%  \begin{subfigure}{0.3\textwidth}
+%  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
+%  \caption{}\label{fig:sf_qz_correlation}
+%  \end{subfigure}   
+%  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
+%  points meant to represent monomer head groups. We added a similar amount of noise to 
+%  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
+%  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
+%  peaks. (b) When we correlate the distance between points within each column, the 
+%  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
+%  intensity between the center and outer peaks. (c) Correlation of the distance between
+%  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
+%  \end{figure}
+
+%  The $q_r$ and $q_z$ profiles of R-$\pi$ generated from a simplified parallel displaced trajectory
+%  where we represented monomer head groups with point scatterers exhibits sharp peaks with
+%  no breadth. Figure~\ref{fig:sf_qy_nocorrelation} and~\ref{fig:sf_qz_correlation} shows
+%  the $q_y$ and $q_z$ cross-sections of R-$\pi$ generated by simulating the structure 
+%  factor of the trajectory. The distance between peaks in the $q_y$ cross-section is 
+%  equivalent to the distance between pores in real space.
+
+  % BJC11: probably unnecessary discussion. Could add to supplemental.
+%  Correlation between scatterers increase the intensity of R-$\pi$ and broadens
+%  its $q_z$ cross-section. In the simplified system described above, we added
+%  Gaussian noise to the mean positions of an equally spaced column of points. 
+%  This ignores any interaction head groups might have with each other. To remedy
+%  this, we placed points in the $z$-direction by drawing random samples from a
+%  multivariate normal distribution defined by the mean positions of an equally
+%  spaced column of points. We gave the distribution at each point along the column
+%  the same standard deviation, $\sigma_z$, shown in Table~\ref{table:quenched_disorder}.
+%  We defined a covariance matrix such that the covariance, $v$, of the distance, 
+%  $d$, between scatterers decays exponentially from $v$ according to the equation
+%  $ve^{-d/L}$, where $L$ is the correlation length. We simulated the structure
+%  factor of a simple system built as described above with a correlation length of
+%  30 $\AA$. We chose 30 $\AA$ in order to exaggerate the effect of correlation
+%  length for visual purposes. Subsequent structure factor calculations are all
+%  done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section
+%  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$
+%  cross-section (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in
+%  experiment. Additionally, there is a near 20\% increase in the maximum
+%  intensity of R-$\pi$ when the distances between scatterers are correlated.
 
   %BJC8: Can show correlation effect on intensity in supporting info
-
-  The correlation length of vertically stacked scatterers in our atomistic simulations
-  are in reasonable agreement with experiment. Since it is not feasible for us to
-  simulate membranes with much taller columns for increased $q_z$ resolution, and
-  because the peak shape is convoluted by the extremely intense maximum of
-  R-$\pi$, we measured correlation length by plotting the one-dimensional pair
-  distribution function, $g(z)$, for the centers of mass of monomer phenyl rings
-  (Figure~\ref{fig:correlation}). In order to calculate $g(z)$, we averaged all
-  $z$-slices of the 3D correlation function within 2.1 \AA~of $g(0, 0, z)$. In this
-  way we are trying measure correlation between head groups within the same column.
-  %We used this 
-  %information to understand how far apart monomers stack within monomer columns and
-  %the degree to which they are correlated.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
-  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
-  \end{subfigure}  
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{z_correlation_offset.png}
-  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
-  \end{subfigure}  
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
-  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
-  \end{subfigure}  
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
-  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
-  \end{subfigure}  
-  %MRS10: should say something here about whether this is consistent or not with experiement (and why/why not)
-  %MRS10: maybe include correlation lengths as well calculated from these, and compare to experiment?
-I know it's in the table as well, but seems missing here.
-1D correlation functions are given, but not how that data proves central points.
-  \caption{1D correlation functions of the center of masses of aromatic head
-	  groups, $g(z)$, show decaying oscillatory behavior. We calculated the
-	  correlation length by fitting a decaying exponential function
-	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
-	  correlation length is longer for ordered basin systems
-	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
-	  correlation length for (d) because there are no clear peaks. We assume that its
-	  correlation is less than the vertical distance between monomers.}\label{fig:correlation}
-  \end{figure}
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{cccc}
-  \toprule
-  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
-  \midrule
-  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
-  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
-  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
-  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
-  Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
-  \bottomrule
-  \end{tabular}
-  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
-  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
-  \label{table:correlation_length}
-  \end{table}
-
-  Monomers in the ordered basin stack closer together than those in the
-  disordered basin (Table~\ref{table:correlation_length}). We calculated the
-  equilibrated vertical distance, $\mathit{d}_{equil}$, between monomers using
-  Equation~\ref{eqn:decaying_sinusoid}. Monomers in the ordered basin stack ca.
-  0.2 and 0.3 \AA~closer than those built in the disordered basin in the
-  sandwiched and parallel displaced configurations respectively. The distance
-  %MRS10: OK this is finally addressed here, but it it's sort of buried in the middle of a paragraph, and not laid out as an outlined point, whereas most readers would ask about it early.
-  between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all
-  cases, with disordered basins at the high part of that range, 0.2 and 0.3
-  \AA~more distant.
-  % MRS9: GAFF could OVER predict pi-pi stacking, best to include citations here
-  % that it does indeed overpredict.  % BJC9: Turns out the Jankowski group was using oplsaa, not GAFF (they said
-  % GAFF to me). Will search for other references.
-  This behavior is not surprising since GAFF models atoms as point charges and
-  does not appropriately model the aromatic $\pi-\pi$ interactions which would
-  make it more energetically favorable for the monomers to stack closer together.
-  Additionally, it is possible that the tails prevent close stacking of monomer
-  head groups and we do not achieve the timescales necessary for them to
-  rearrange into a necessarily more tightly packed configuration. We equilibrated
-  the system at 500K in an attempt to coerce the tails into a more tightly packed
-  configuration, however we saw no improvement over our 300K models. See section
-  S-TBD for details. Overall, head groups in the ordered basin systems pack 
-  closest together and are likely the best choice for transport studies.
-
-  %We expect that when monomers stack closer together, steric clashes
-  %force head groups to orient in a more ordered fashion. If head groups in our model stayed 3.7 \AA
-  %apart, we may actually see higher values of R-$\pi$ due to enhance order.
-
-  %MRS7: other hypothesis about stacking that comes from Matt's implications is that it may have to do with
-  %tail entropy, and for some reason ours is frozen in a configuration that is a bit too far apart. I see you talk about this later, but might need to     be brought up again.
-  %BJC6: tried to work that in a bit. But as you say, there is more about this point later. I could reference it here.
-
-  The correlation length of the parallel displaced, ordered basin system shows
-  the closest agreement with experiment (Table~\ref{table:correlation_length}).
-  Note that its correlation length ($L$ = 14.5 \AA) is larger than what we would 
-  expect by inverting the FWHM of the $q_z$ cross-section of R-$\pi$ shown in 
-  Figure~\ref{fig:sim_zsection_fit} ($L$ = 1 / 0.163 = 6.1 \AA). The reason is
-  likely a combination of artificial broadening caused by the overlap of 
-  R-alkanes and R-$\pi$ as well as errors in the fit due to low simulated 
-  XRD resolution. We calculated the correlation length of each system using 
-  Equation~\ref{eqn:decaying_exponential}. We could not extract a reliable 
-  correlation length from the disordered parallel displaced configuration since
-  the peaks do not show clear patterns that can easily be fit to an exponential
-  decay. The correlation length of both sandwiched systems is relatively low
-  because the height of the first peak of $g(z)$ is so high.
-
-  % BJC9: Got rid of references to R-pi intensity in following paragraph because
-  % I can't directly compare R-pi between two simulations starting from different
-  % initial configs w/ different velocity randomizations.
-  The system size, in the $z$-direction, does not significantly alter $g(z)$. 
-  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
-  system may be necessary to fully capture the correlation function. We 
-  equilibrated a sandwiched system with twice as many monomers per column 
-  so that the system size doubled in the $z$-direction. The correlation length 
-  increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. Visually, the
-  correlation functions are nearly identical and oscillatory behavior persists
-  throughout $g(z)$ in both cases (See Figure~S-\ref{S-fig:z_correlation_overlay}).
 
@@
 
-  Increased thermal noise in the $z$-direction will reduce the intensity
+  Increasing thermal noise in the $z$-direction will reduce the intensity
   of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
-  thermal noise of our simple parallel displaced system in the $z$-direction by
+  thermal noise of the simplified parallel displaced system in the $z$-direction by
   12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of 
@@
   intensity, the 3 cross-sections have the same shape 
-  (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp Bragg-like peaks are
+  (Figure~\ref{fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
   not consistent with experiment.
@@
   intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
-  diffraction patterns smooths out. 
-  This is shown by creating 
-  simple systems 
+  diffraction patterns smooths out. This is shown by creating a simplified sandwiched
+  configuration, where each head group is represented by a point scatterer,
+  %simple systems 
   %MRS10: simple systems is not very exact. Point scatters that represent the head groups?
-  with varying
-  amounts of association between columns. In the low limit, the center of mass
-  of columns are situated at the same $z$-coordinate. 
-  %MRS10: unnecessary line?
-  This is how all simple
-  systems have been created up to this point. We allow increasing independence of
-  columns by randomly shifting each column in the $z$-direction according to a uniform
-  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges
-  between 0 and 1. We limit this discussion to the sandwiched configuration since
-  it is not feasible for columns in the parallel displaced configuration, as we
-  have set them up, to move past each other. When $f = 1$, the columns move 
-  independently and the $q_r$ cross-section smooths out 
-  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp
-  peaks. The intensity of R-$\pi$ decreases with increasing column independence.
-  We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$ versus when
-  $f=0$. It is likely that the discrepancy between the intensity of R-$\pi$ 
-  generated from our simulations versus experiment is primarily due to highly 
-  correlated columns in our initial configurations.
+  %BJC11: It feels redundant and wordy saying the above rather than simple systems.
+  with varying amounts of association between columns. In the low limit, 
+  the center of mass of columns are situated at the same $z$-coordinate. 
+  We allow increasing independence of columns by randomly shifting each column
+  in the $z$-direction according to a uniform distribution bounded by (0, 
+  $f \times \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We limit 
+  this discussion to the sandwiched configuration since it is not feasible for
+  columns in the parallel displaced configuration, as we have set them up, to
+  move past each other. When $f = 1$, the columns move independently and the
+  $q_r$ cross-section smooths out (Figure~\ref{fig:column_displacement}). Any
+  amount of dependence results in sharp peaks. The intensity of R-$\pi$ decreases
+  with increasing column independence. We see an 8-fold decrease in the intensity
+  of R-$\pi$ when $f=1$ versus when $f=0$. It is likely that the discrepancy 
+  between the intensity of R-$\pi$ generated from our simulations versus experiment
+  is primarily due to highly correlated, glassy columns in our initial configurations.
 
@@
 
-  The columns in the simulated system are highly correlated. If the columns were
-  uncorrelated, $g(z)$ of the ordered sandwiched system would very closely resemble 
-  Figure~\ref{fig:z_correlation_sandwich} when we average all $z$-slices of the
-  3D correlation function. When we include all $z$-slices in $g(z)$ for our system,
-  the function shows oscillatory behavior and the correlation length nearly triples
-  to 12.41 $\pm$ 0.69 \AA. (Figure~\ref{fig:z_correlation_fullbox}). Since all 
-  columns in our initial configuration are started at the same $z$-coordinate, 
-  $g(z)$ on average exhibits correlation of head groups with other head groups
-  within the same column, with head groups in other columns within the same pore, 
-  and with head groups in different pores.
-
-  %BJC9: Note that the magnitude of the correlation function is much lower than 
-  % in figure 10a. That's because many of the z-slices are zero when you include
-  % all of them.
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.png}
-  \caption{When we average all $z$-slices of the 3D correlation function, the 
-  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
-  \end{figure}
-
   Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
-  cross-section of R-$\pi$ to, somewhat counterintuitively, to decrease. Using a system with uncorrelated columns,
-  we modified the disorder in both the $r$ and $\theta$ directions by multiplying
-  their values by a factor of 0.5 and 2 (Figure~\ref{fig:qy_fwhm}). When we cut
-  the noise in half, the FWHM increases by 88\%. When we double the noise, the
-  FWHM decreases by 51\%.
+  cross-section of R-$\pi$ to, somewhat counterintuitively, to decrease. Using a 
+  %BJC11: ^ Not sure this is counterintuitive to people thinking in reciprocal space.
+  system with uncorrelated columns, we modified the disorder in both the $r$ and
+  $\theta$ directions by multiplying their values by a factor of 0.5 and 2 
+  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
+  by 88\%. When we double the noise, the FWHM decreases by 51\%.
 
@@
   \end{figure}
+
+  The columns in the atomistic simulated system are highly correlated. If the columns were
+  uncorrelated, $g(z)$ of the ordered sandwiched system would very closely resemble 
+  Figure~\ref{fig:z_correlation_sandwich} when we average all $z$-slices of the
+  3D correlation function. When we include all $z$-slices in $g(z)$ for our system,
+  the function shows oscillatory behavior and the correlation length nearly triples
+  to 12.4 $\pm$ 0.7 \AA. (Figure~\ref{fig:z_correlation_fullbox}). Since all 
+  columns in our initial configuration are started at the same $z$-coordinate, 
+  $g(z)$ on average exhibits correlation of head groups with other head groups
+  within the same column, with head groups in other columns within the same pore, 
+  and with head groups in different pores.
+
+  %BJC9: Note that the magnitude of the correlation function is much lower than 
+  % in figure 10a. That's because many of the z-slices are zero when you include
+  % all of them.
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.png}
+  \caption{When we average all $z$-slices of the 3D correlation function, the 
+  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
+  \end{figure}
+
+  We can explain the discrepancies between R-$\pi$ seen experimentally
+  and in simulation using what we have shown in this section. The stacking
+  distance between monomer head groups is too large, likely due to failures
+  of the forcefield to appropriately model $\pi-\pi$ interactions. The intensity
+  of the simulated R-$\pi$ is too high, which may be a consequence of too much
+  ordering in the $z$-direction in addition to high degrees of correlation 
+  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
+  which is also likely a consequence of highly correlated columns.
 
@@
 
+  Because disorder among head groups in the simulated atomistic systems is largely
+  determined by each system's quenched configuration, one would need to average an
+  ensemble of simulations in order to optimally match the experimental WAXS pattern. 
+  Both the initial configuration and initial velocity randomization lead to 
+  different quenched configurations every time we run an equilibration simulation.
+  Although the simulated XRD pattern changes dynamically as we simulate the system
+  due to thermal fluctuations, its features are largely determined by the initial 
+  quenched configuration. Here we assume that the timescales for large scale 
+  rearrangements of the system are much longer than what we can feasibly simulate. 
+  As a result, it will be difficult to exactly reproduce the work here, but we are
+  confident that one can draw the same conclusions using our methodology.
+
   %MRS10: Maybe rephrases; rather than talking about building a better
   %model, you can summarize the differences that could explain the discrepancy between experiment and simulation.
-  We can use what we learned above in order to construct a better model,
-  however there will still be shortcomings. We can decrease the intensity of
-  R-$\pi$ if we incorporate more $z$-directional noise, which may come from
-  increasing the system's temperature. 
-  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
-  % temperature? Is decreasing the force constant between bonds viable? 
-  We can also decrease the intensity of R-$\pi$, in addition to smoothing the
-  $q_y$ cross-section by creating initial configurations whose columns are
-  displaced randomly in the $z$-direction. We can achieve better averages if we
-  create systems with more pores in the unit cell. In order to make head groups
-  stack closer together, we can adjust the force field parameters for aromatic 
-  carbons. Ultimately, we will need extremely long simulation times, or enhanced
-  sampling techniques so that monomers within columns can rearrange and sample
-  enough independent configurations to generate a robust simulated XRD pattern.
+  %BJC11: tried above.
+%  We can use what we learned above in order to construct a better model,
+%  however there will still be shortcomings. In order to make head groups stack
+%  closer together, we can adjust the force field parameters for aromatic 
+%  carbons.  We can decrease the intensity of R-$\pi$ if we incorporate more
+%  $z$-directional noise, which may come from increasing the system's temperature.
+%  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
+%  % temperature? Is decreasing the force constant between bonds viable? 
+%  We can also decrease the intensity of R-$\pi$, in addition to smoothing the
+%  $q_y$ cross-section by creating initial configurations whose columns are
+%  displaced randomly in the $z$-direction. We can achieve better averages if we
+%  create systems with more pores in the unit cell. Ultimately, we will need extremely
+%  long simulation times, or enhanced sampling techniques so that monomers within
+%  columns can rearrange and sample enough independent configurations to generate
+%  a robust simulated XRD pattern.
 
@@
 
-  %BJC10: I think this belongs somewhere in this section.
-  The simulated XRD patterns of the parallel displaced configurations show additional
-  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
-  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
-  for the same reason as R-double. It is possible that parallel displaced monomers contribute
-  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.
+  R-double does not appear in any of the simulated diffraction patterns generated using
+  the systems simulated up to this point. Here we hypothesize a few initial 
+  configurations which may lead to the appearance of R-double and show that we cannot
+  achieve a long-term stable system that exhibits R-double without the inclusion of 
+  small amounts of water in the pores.
 
@@
   the position of monomers in parallel displaced configurations alternate every other layer, 
-  we know that such a screw axis type configuration will not produce R-double, but only off-axis 
+  we know that such a configuration will not produce R-double, but only off-axis 
   reflections at the same $q_z$ value~\cite{harburn_atlas_1975}. There is not a unique solution
@@
   We have proposed configurations that result in the appearance of R-double below, and we can 
-  speculate which makes the most physical sense. We explore both dry and wet configurations.
+  speculate which makes the most physical sense. We show that we cannot achieve a long-term
+  stable system that exhibits R-double without the inclusion of small amounts of water in the pores.
+
+    %BJC10: I think this belongs somewhere in this section.
+    %BJC11: might be covered well enough in above 
+%  The simulated XRD patterns of the parallel displaced configurations show additional
+%  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
+%  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
+%  for the same reason as R-double. It is possible that parallel displaced monomers contribute
+%  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.
 
@@
   We can produce R-double if we rotate monomers with respect to vertically adjacent monomers. 
-%  Our final hypothesized dry configuration which produces R-double focuses on the orientation of the tails. 
   In this configuration, monomers are rotated so that the vector created by the  
@@
 
-  Adding water to the system appears to facilitate the appearance of R-double,
+  Adding water to the system appears to promote the appearance of R-double,
   through the creation of hydrogen bonding of water to carboxylate groups of
@@
   a modest number of occurrences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
-  Peaks in the distributions represent the scenario where a monomer head group shares a 
-  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
+  In order to create Figure~\ref{fig:pore_hbonds}, we binned the $z$-positions of the
+  center of mass of the monomer head groups into 20 bins, the same number as the monomers
+  per columns. This works relatively well since there is a high degree of correlation between
+  columns in our system. Peaks in the distributions represent the scenario where a monomer head group
+  shares a water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
   we calculated the discrete Fourier transform of the distributions which we used as a rough 
   indicator of whether the head group arrangement will lead to R-double. We see the 
-  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
-  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.
-
-  It is thus most likely that R-double originates from water molecules as described above, as it is the 
-  only mechanism that can be observed without externally restraining positions. The extent of the hydrogen
-  bonding network that forms is largely determined by the accuracy of the forcefield. It is 
-  possible that a more realistic forcefield would make the effect stronger or weaker. If 
-  this is truly the mechanism, it implies that the system studied by Feng et 
-  al.\cite{feng_scalable_2014,feng_thin_2016} was not truly a thermotropic Col\textsubscript{h}
-  phase. Rather, they were very low water content H\textsubscript{II} phases unintentionally
-  created due to the neat monomers' hydroscopicity. This detail may therefore be important for reproducing
-  the results of Feng et al.
+  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 
+  0.75 $\AA^{-1}$ are clearly distinguishable, meaning there is periodicity at twice
+  the $\pi$-stacking distance.
+
+  Of all the configurations tested, it is most likely that R-double is induced by water
+  molecules as described above since it is the only mechanism that can be observed without
+  position restraints. The extent of the hydrogen bonding network that forms is largely 
+  determined by the accuracy of the forcefield. It is possible that a more realistic force
+  field would make the effect stronger or weaker. If this is truly the mechanism, it implies
+  that the system studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} was not 
+  truly a thermotropic Col\textsubscript{h} phase. Rather, they were very low water content
+  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity.
+  This detail may therefore be important for reproducing the results of Feng et al.
 
@@
   each other that hydrogen bond with a shared water molecule are drawn closer
-  together. Blue monomers were stacked above orange monomers in the initial configuration.
-  (c) Monomers in each column are numbered from 1--20. For simplicity, we define a layer to
-  be composed of all same-number monomers. Peaks in the distributions indicate
-  a shared hydrogen bonded water molecule between a monomer head group and one in the layer
-  vertically above it. For example, in Pore 1, monomer 7 shares a hydrogen bond with
-  a monomer in layer 8 (pictured in (b)). In this scenario, monomers are no longer evenly
-  spaced in the z-direction since they are pulled closer together by hydrogen bonds. 
-  (d) We performed discrete Fourier transforms on each distribution in (c). In all cases,
-  the strongest peak represents periodicity every layer. In Pore 1, there is also periodicity
-  every other layer as indicated by the strong peak at 0.5 layers$^{-1}$. In this case, the
-  center of mass of two adjacent pairs is separated by twice the average monomer stacking 
-  distance, while the four monomers involved are unequally spaced. These conditions may
-  give rise to R-double.}\label{fig:hbonds}
+  together in the $z$-direction. Blue monomers were stacked above orange monomers in the
+  initial configuration. (c) We group the $z$-coordinate of the center of mass of monomer
+  head groups into 20 bins. Peaks in the distributions indicate a shared hydrogen bonded
+  water molecule between a monomer head group and one in the bin vertically above it. 
+  The distance between the peaks roughly corresponds to the distance between pairs of 
+  monomers. The distance between peaks in pore 1 (indicated by arrows) is equal to two 
+  times the $\pi$-stacking distance. In this scenario, monomers are no longer evenly spaced
+  in the $z$-direction since they are pulled closer together by hydrogen bonds. (d) We 
+  performed discrete Fourier transforms on each distribution in (c) In Pore 1, there 
+  also periodicity every 8.3 $\AA$, twice the $\pi$-stacking distance, as indicated by the
+  intensity at 0.76 $\AA^{-1}$). In this case, the center of mass of two adjacent pairs 
+  is separated by twice the average monomer stacking distance, while the four monomers 
+  involved are unequally spaced. These conditions may give rise to R-double.}\label{fig:hbonds}
   \end{figure}

### 2018-08-16 analysis/hbond_pairing.py

@@ -124,17 +124,26 @@ if __name__ == "__main__":
         # single[i] = n
         # above_and_below[i] = N
 
+    z_avg = np.mean(sys.t.unitcell_vectors[:, 2, 2])
+    print(z_avg)
+    z = np.linspace(0, z_avg, 20)*10 # angstroms
+
     fig1, ax1 = plt.subplots(2, 2)
     for i in range(2):
         for j in range(2):
-            ax1[i, j].plot(np.linspace(1, nlayers, nlayers), np.mean(inter[(2*i + j)*nlayers:(2*i + j + 1)*nlayers, :], axis=1), linewidth=2)
+            ax1[i, j].plot(z, np.mean(inter[(2*i + j)*nlayers:(2*i + j + 1)*nlayers, :], axis=1), linewidth=2)
             ax1[i, j].text(.5, .85, 'Pore %d' % (1 + j + 2 * i), horizontalalignment='center', transform=ax1[i, j].transAxes, fontsize=14)
             ax1[i, j].set_ylim(0, 1)
 
-    ax1[1, 0].set_xlabel('Layer', fontsize=14)
-    ax1[1, 1].set_xlabel('Layer', fontsize=14)
+    ax1[1, 0].set_xlabel('$z$-coordinate ($\AA$)', fontsize=14)
+    ax1[1, 1].set_xlabel('$z$-coordinate ($\AA$)', fontsize=14)
     ax1[0, 0].set_ylabel('Average shared\n hbonds', fontsize=14)
     ax1[1, 0].set_ylabel('Average shared\n hbonds', fontsize=14)
+
+    ax1[0, 0].annotate('', xy=(30.5, 0.5), xytext=(30.5, 0.8),
+                arrowprops=dict(facecolor='black', width=1, headwidth=6,shrink=0.2, headlength=6), fontsize=14)
+    ax1[0, 0].annotate('', xy=(39.25, 0.46), xytext=(39.25, 0.76),
+                arrowprops=dict(facecolor='black', width=1, headwidth=6,shrink=0.2, headlength=6), fontsize=14)
 
     plt.tight_layout()
     plt.savefig('pore_hbonds.png')
@@ -143,6 +152,7 @@ if __name__ == "__main__":
     block_length = 2  # insert this many zeros after each entry in layers
     pores = 4
[…]

### 2018-08-17 Ben_Manuscripts/structure_paper/Draft.tex

@@
 
-  Adding water to the system appears to promote the appearance of R-double,
-  through the creation of hydrogen bonding of water to carboxylate groups of
-  consecutive layers. We added water to the parallel displaced and sandwiched
+  The addition of water to the system appears to promote the appearance of R-double.
+#  through the creation of shared hydrogen bonds between water molecules and carboxylate
+#  groups of vertically stacked monomers. 
+  We added water to the parallel displaced and sandwiched
   configurations in the ordered basin and equilibrated them according to the wet

### 2018-08-18 Ben_Manuscripts/structure_paper/Draft.tex
More comments.

--- 2018-08-16 Ben_Manuscripts/structure_paper/Draft.tex
@@
 
-  We further refined our structural understanding of the system by simulating X-ray 
+  We 
+  %MRS12: sounds too much like structure refinement
+  %further refined our structural understanding 
+  can better understand the structure of the system by simulating X-ray 
   diffraction patterns produced from equilibrated MD trajectories and comparing them
@@
   per pore in the parallel displaced and sandwiched configurations at 300 K in the 
-  ordered and disordered basins. We generated simulated patterns using the equilibrated
+  ordered and disordered basins,
+  %MRS12: added
+  as those were the most consistent with the most unambiguous X-ray diffraction patterns, the pore-to-pore spacing and the stacking distance.
+We generated simulated patterns using the 
+  %MRS12: maybe refer to part of methods where we determined which ones were equilibrated?  Also, maybe say locally equilibrated? Since we know it might be only metastable. 
+equilibrated
   portion of each simulation trajectory. There are two important factors to take into
@@
   is due to the angle averaging of the 3D structure factor around the $q_z$-axis, meaning
-  there are fewer samples as  $q_r$ approaches 0. The amount of samples to converge along
+  there are fewer samples as  $q_r$ approaches 0. The amount of samples 
+  %MRS12: added
+  required to
+  to converge along
   the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}. 
   More importantly, our simulations do not appear to be long enough to sample truly 
-  independent configurations within their respective metastable basins (See 
+  independent configurations within their respective metastable basins (see 
   section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the
@@
 	broad R-$\pi$ reflection. Quantitative comparisons of the relative intensities of reflections of
-	interest are presented in Table~\ref{table:relative_inensities_300K}. In both XRD patterns generated
+	interest are presented in Table~\ref{table:relative_intensities_300K}. In both XRD patterns generated
 	from parallel displaced patterns, there is a faint line across $q_z \sim 0.7~$\AA$^{-1}$, half
@@
 	in any of the simulated patterns.}~\label{fig:XRDsim} 
+        %MRS12: I would repeat the labels from figure 3.  Minimum, need to refer back to that figure so they know where to find the definitions of the lables. 
   \end{figure}
@@
   are key qualitative and quantitative differences between the experimental and simulated
-  locations and intensities of each major reflection. We measured the intensity and location
-  of each simulated reflection relative to its experimental counterpart 
-  (Table~\ref{table:relative_inensities_300K}). Our methods for measuring the intensity of
-  each reflection are presented in section S-\ref{S-section:xrd_intensities}.
+  locations and intensities of each major reflection. The integrated intensity and location
+  of each simulated reflection relative to its experimental counterpart are shown in  
+  Table~\ref{table:relative_intensities_300K}. Our approach for measuring the intensity of
+  each reflection are described in section S-\ref{S-section:xrd_intensities}. %MRS12: should that be in Methods instead of suporting?  Not sure.
 
@@
 %  does not appear in any patterns, and thus has no measurable intensity.}
-%  \label{table:relative_inensities_300K} 
+%  \label{table:relative_intensities_300K} 
 %  \end{table}
@@
   \end{tabular}
+  %MRS12: question: is the normalization for the simulated systems the same, no matter if disordered, etc.  If not chosen to be exactly the same, how different are they? 
   \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
-  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
+  intensity of R-alkanes in each pattern equals 1, show R-$\pi$ reflections that are significantly higher 
   than experiment and R-spots reflections that are slightly lower than experiment. R-double
-  does not appear in any patterns, and thus has no measurable intensity.}
-  \label{table:relative_inensities_300K} 
+  does not appear in any simulated patterns, and thus has no measurable intensity.}
+  \label{table:relative_intensities_300K} 
   \end{table}
@@
 %  of each reflection of interest between experimental and simulated patterns. 
-%  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
+%  Table~\ref{table:relative_intensities_300K} shows the relative intensities of each reflection for 
 %  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
@@
   % GAFF forcefield paper? Need to actually check it though.
-
+  %MRS12: first pass.  
+  We reach this conclusion because alkane
+  parameters in GAFF and AMBER forcefields are generally reproduce data well.~\cite{original_gaff_paper} 
+  %MRS12: Citation is: https://doi.org/10.1002/jcc.20035  could also cite: https://pubs.acs.org/doi/pdf/10.1021/ct200731v
+  %MRS12: below - say what appears close means?  radius of max is X vs Y.
   R-alkanes appears close to its expected location. In all cases, the maximum intensity
   of R-alkanes appears at a $|\mathbf{q}|$ value only slightly higher than experiment. 
-  We expect that the exact location of R-alkanes will not be perfect in our simulations
-  since the simulated diffraction patterns are interpolated between a finite number of
-  bins in each frequency dimension. We can achieve higher resolution with a larger
-  system size, however we are satisfied with the packing distances shown by our simulations.
-  %BJC11: I could integrate a 3D correlation function to get a better value
+  %MRS12: different pass?
+Though need to specify WHAT the error is.
+Can't be intensity, since that is what we are normalizing by, so is it LOCATION of the intensity?
+Also, need to verify the statement is correct.
+Could still good languange if the conclusion was that the binning error was similar in size to errors in the location R-alkane.
+  The error in the simulated diffraction patterns is less that the error due binning in eack frequency direction, so was not further investigated. 
+  %We expect that the exact location of R-alkanes will not be perfect in our simulations
+  %since the simulated diffraction patterns are interpolated between a finite number of
+  %bins in each frequency dimension. 
+  %We can achieve higher resolution with a larger
+  %system size, however we are satisfied with the packing distances shown by our simulations.
+  %BJC11: I could integrate a 3D correlation function to get a better value.
+  %MRS12: saying ``we are satisfied'' opens to claims that reviwers say ``well, I'm not''.  Pass at this above.
 
@@
   % unrelated to the actual pore structure.
-
-  We are not concerned with exactly reproducing the intensity of R-pores since it is a 
-  product of long distance correlations between pores. We are primarily concerned with
-  the structure within pores which is better described by reflections at higher 
-  $|\mathbf{q}|$ values.
-
-  The location of the leading peak of R-pores is geometrically related to the average 
-  distance between pores. However, there is uncertainty in its exact location because
-  the Fourier bin size is so large. We can measure the average distance between columns
+  % MRS12:  Agreed. Rephrased a bit.
+  The agreement in intensity in R-pores obtained here is sufficient for this study because this intensity is primarily controlled by longer-range organization that cannot be captured by simulation of only 4 pores and because we are concered with the with the structure of the individual pores themselves.
+
+  The location of the leading peak of R-pores is directly related to the average 
+  distance between pores. However, there is substatial uncertainty in the exact location 
+  relative to the bin size used for the Fourier space transformation. We can instead 
+  measure the average distance between columns
   with more precision in real space (See Section~\ref{method:pore_spacing}). We showed
@@
   The intensity of R-spots is close to experiment when generated from any of our
-  simulated systems. The appearance of R-spots is inconspicuous in most cases so we
-  assumed that the location of R-spots, in terms of $|\mathbf{q}|$ would coincide with
-  that of R-alkanes, and that it's $q_z$ location should be roughly in line with 
-  R-double (half the $q_z$ location of R-$\pi$) as it appears in the experimental pattern.
+  simulated systems. 
+  Because the R-spots reflection is difficult to distinguish visually as it appears 
+  at the same $|\mathbf{q}|$ as R-alkanes, we calculate 
+  the intensity of R-spots by assuming that its $q_z$ location should be roughly in line with 
+  the experimental R-double, half the $q_z$ distance of R-$\pi$).
+  %The appearance of R-spots is inconspicuous in most cases so we
+  %assumed that the location of R-spots, in terms of $|\mathbf{q}|$ would coincide with
+  %that of R-alkanes, and that it's $q_z$ location should be roughly in line with 
+  %R-double (half the $q_z$ location of R-$\pi$) as it appears in the experimental pattern.
   We measured the intensity of R-spots by radially integrating the simulated
@@
 
-  R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
-  Previous literature has attributed the spots in this particular WAXS dataset as 
-  the product of tilted alkane chains~\cite{feng_scalable_2014}. Here we refute 
-  that explanation and show that the tails do not tilt, but rather pack in a 
-  hexagonal array.
-
-  In order to more clearly study R-spots, we equilibrated an ordered basin sandwiched 
-  configuration at 280K. Many force fields do not obtain the correct equilibrium structure
+  %MRS12: here I'm going to break the rule of the thesis statement, since it reads strangely to have thesis, contradition, repeat thesis, there isn't any evidence. But it flows OK this way.   
+  %R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
+  Previous literature has attributed the R-spots reflection in this particular WAXS dataset as 
+  the result of tilted alkane chains~\cite{feng_scalable_2014}. 
+  %Here we refute that explanation and show that the 
+  We measured the tilt angle of the alkane chains of
+  the 280K system and found that it equilibrates to an average tilt angle of
+  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
+  used to explain R-spots. Similar lack of more than a statistically negligible tilt occured when 
+  we performed the simulations with a number of other starting configurations, obtaining similar results.%MRS12: I know we discussed this earlier; there were a number of things that were done to verify this results was consistent, and I think that a rief summary would help.
+
+  In order to more clearly identify the structural reasons for R-spots, we equilibrated an ordered basin sandwiched 
+  configuration at 280K to moderately increase the order and therefore intensity. 
+  Many force fields do not obtain the correct equilibrium structure
   at precisely the experimental temperature. Wang et al. highlighted the shortcoming of 
@@
   our membrane system, simulated at 300K, is under-structured in the tail region compared
-  to the experimental structure at 300K. We found that lowering the temperature better 
+  to the experimental structure at 300K. We found that lowering the temperature indeed better 
   resolved R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' 
@@
 
-  Evidence from the simulations strongly suggests that the R-spots signal is not a 
-  result of alkane chain tilt. We measured the tilt angle of the alkane chains of
-  the 280K system and showed that it equilibrates to an average tilt angle of
-  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
-  used to explain R-spots.
-
-  Although the monomer tails do not tilt, R-spots still originates from 
-  them. By removing all non-tail atoms from the trajectory and simulating a
-  diffraction pattern with the remaining atoms, we were able to isolate the
-  cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
-
-  %BJC11: need to rephrase -- "strongly suggests" used two paragraphs prior
-  The evidence strongly suggests that R-spots occurs because tails pack 
-  together hexagonally. We plotted the center of masses of the first four tail 
-  atoms of all tails (Figure \ref{fig:centroids}). We measured the angle between
-  each center of mass and its nearest neighbor center of masses with respect to
-  the $xy$ plane of the membrane. We see distinct peaks in the distribution of
-  these angles located ca. $-60\degree$, $0\degree$, and $60\degree$ which is
-  consistent with a hexagonally packed configuration (Figure~\ref{fig:layered_tails}). 
-  %MRS10: is it importat that the ordering dies off? IF there is ordering, it will show in the spectra, and it doesn't matter that it dies off in other parts of the spectra.
-  %BJC10: I only addressed this because Matt wanted a more thorough characterization of tail order 
-  This ordering dies off at the tail ends, where there is more space to fill 
-  causing them to pack nearly isotropically. See Section~S-\ref{S-tail_packing}
-  for a more detailed explanation of the calculation and packing distributions
-  generated from different sections of the tails.
+  The Evidence from the simulations strongly suggests that the R-spots signal
+ is not a 
+  result of alkane chain tilt.
+
+  The evidence from simulations strongly suggest that the source of
+  the R-spots reflection is packing of the tails in a hexagonal array.
+  First, we demonstrate R-spots comes primarily from the tails, by
+  removing all non-tail atoms from the trajectory and simulating the
+  XRD diffraction pattern with the remaining atoms, which preserves
+  R-spots(Figure~\ref{fig:tails_rzplot}).  Next, we plotted the center
+  of masses of the first four tail atoms of all tails (Figure
+  \ref{fig:centroids}). We measured the angle between each center of
+  mass and its nearest neighbor center of masses with respect to the
+  $xy$ plane of the membrane. We see distinct peaks in the
+  distribution of these angles located ca. $-60\degree$, $0\degree$,
+  and $60\degree$ which is consistent with a hexagonally packed
+  configuration (Figure~\ref{fig:layered_tails}).  This ordering is
+  primarily in the parts of the tail proxmal to the heads, and dies
+  off at the tail ends, where there is more space to fill causing them
+  to pack nearly isotropically. See Section~S-\ref{S-tail_packing} for
+  a more detailed explanation of the calculation and packing
+  distributions generated from different sections of the tails.
 
@@
   The position, shape and intensity of R-$\pi$, generated from simulations at 300K, are 
-  qualitatively and quantitatively different than experiment. The reflections appear
-  at lower $q_z$ values, they are more intense and the shape of its cross-sections, 
-  especially in the $q_r$ direction are different relative to the experimental system
-  (See Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the simulated
-  XRD generated from the ordered parallel displaced configuration as an example). In 
-  this section, we explore the various contributions to these discrepancies, and use what
-  we've learned to speculate on improvements to our initial configurations and simulation
-  procedures.
+  qualitatively similar to experiment, but have significant quantitative differences. The reflections appear
+  at lower $q_z$ values, they are more intense, and the shape of its cross-sections, 
+  especially in the $q_r$ direction are different relative to the experimental system.
+  For comparison, see Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the simulated
+  XRD generated from the ordered parallel displaced configuration as an example. In 
+  this section, we explore the various contributions to these discrepancies, and use this information to 
+  speculate on what reasonable differences in the simulations could explain the discrepancies.
 
@@
   experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
-  the FWHM of the simulated pattern agrees with experiment within error, however
-  the fit to the simulated data is obscured by the three sharp peaks which appear
+  the FWHM (full width at half maximum) of the simulated pattern agrees with experiment within error. However
+  the fit to the simulated data is affected by the three sharp peaks which appear
   near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
@@
   cross-section. Additionally, peak of the simulated $q_z$ cross-section is 
-  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
+  located at a somewhat lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
   \end{figure}
@@
 %  displaced system to 15 times too high in the ordered sandwiched configuration 
-%  (Table~\ref{table:relative_inensities_300K}).
+%  (Table~\ref{table:relative_intensities_300K}).
 
@@
   %BJC11: Below is in methods but might be worth restating here? 
+  %MRS12: no, OK here.
 %  based on the center of mass of each monomer head group. In order
@@
   monomers is greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
-  basins at the high part of that range, 0.2 and 0.3 \AA~more distant. This behavior is
-  not surprising since GAFF models atoms as point charges and  % BJC11: need reference
-  does not appropriately model the aromatic $\pi-\pi$ interactions which would make it
-  more energetically favorable for the monomers to stack closer together. Additionally, 
-  it is possible that the tails prevent close stacking of monomer head groups and we do
+  basins at the high part of that range and are on average 0.2 and 0.3 \AA~more distant. This behavior is
+  not surprising since GAFF models atoms as point charges and  % BJC11: need reference %MRS12: just cite the GAFF paper.
+  does not appropriately model the aromatic $\pi-\pi$ interactions, which make it
+  more energetically favorable for the monomers to stack closer together. 
+  It is also possible that the tails prevent close stacking of monomer head groups and we do
   not achieve the timescales necessary for them to rearrange into a necessarily more
-  tightly packed configuration. We equilibrated the system at 500K then annealed it to 300K
+  tightly packed configuration. However, we equilibrated the system at 500K then annealed it to 300K
   in an attempt to coerce the tails into a more tightly packed configuration, however 
-  we saw no improvement over our 300K models. See section S-TBD for details.
+  we saw no improvement in packing distance over our 300K models. See section S-TBD for details.
 
@@
   In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
-  system may be necessary to fully capture the correlation function. We 
+  system may be necessary to fully capture the correlation function. We therefore 
   equilibrated a sandwiched system with twice as many monomers per column 
   so that the system size doubled in the $z$-direction. The correlation length 
-  increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. Visually, the
+  increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
   correlation functions are nearly identical and oscillatory behavior persists
@@
   The broadening of the $q_z$ cross-section of R-$\pi$ is related to $z$-directional
-  correlation between scatters within monomer columns. One can determine the correlation length as the
+  correlation between scatters within monomer columns. The correlation length varies as the
   inverse of the full width at half maximum (FWHM) of the $q_z$ cross-section of R-$\pi$.
@@
   are in reasonable agreement with experiment. Since it is not feasible for us to
-  simulate membranes with much taller columns, for increased $q_z$ resolution of our
+  simulate membranes with much taller columns in order to obtain increased $q_z$ resolution of our
   simulated XRD patterns, and because the simulated peak shape is convoluted by the
@@
   % could say "distance covariance"
-  Overall, we believe our simulations exhibit a realistic amount of distance correlation
-  between head groups within each column. The difference in the FWHM of the $q_z$ 
+  Overall, we believe our simulations exhibit a realistic amount of distance correlation in the direction parallel to the pore axis between head groups within each column.
+The difference in the FWHM of the $q_z$
   cross-section of R-$\pi$ between experiment and simulation is less than one bin size
   (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). The more 
-  prevailing difference between the two cross-sections is their maximum intensity which
+  signficant difference between the two cross-sections is their maximum intensity which
   we study in more detail below.
@@
   \caption{1D correlation functions of the center of masses of aromatic head
-	  groups, $g(z)$, show decaying oscillatory behavior. We calculated the
+	  groups, $g(z)$, show decaying oscillatory behavior and have consistent correlation lengths with experiment. We calculated the
 	  correlation length by fitting a decaying exponential function
@@
 	  correlation length for (d) because there are no clear peaks. We assume that its
-	  correlation is less than the vertical distance between monomers.}\label{fig:correlation}
+	  correlation length is less than the vertical distance between monomers.}\label{fig:correlation}
   \end{figure}
@@
   FWHM (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
-  Additionally, we model each atom with a Gaussian sphere of electron density. 
-  The true electronic structure is likely much more complicated. However, we can
-  explore reasons for which differences in the simulation structure could change
+  Additionally, we model each atom with a Gaussian sphere of electron density, which is a simplification. 
+  However, we can explore reasons for which differences in the simulation structure could change
   the peak shapes and intensities to be in better agreement with experiment.
@@
   present in the atomistic system, which we applied to the simplified systems, are
-  given in Table~\ref{table:quenched_disorder}. The magnitude of quenched disorder
-  is greater than thermal disorder.
+  given in Table~\ref{table:quenched_disorder}. The quenched disorder, the deviation of monomers from idealized 
+  symmetric configurations, several times greater than thermal disorder, the deviations of the monomers during the production simulations.
+  %MRS12: when reworking the first part of the simulation, our hypothesis for the REASONS behind the quenched disorder will ahave to be addressed.
+The two options are 1) the quenched disorder is just thermal disorder whose transition timescales we can't reach, and 2) the system if simulated for miliseconds/seconds would still be glassy.
+It PROBABLY should go before here, when it's first described.
 
@@
   \caption{Deviation of the positions of the center of mass of head groups from their average
-  positions (Thermal Disorder) as well as their idealized positions (Quenched Disorder) to use 
+  positions (thermal disorder) as well as their idealized positions (quenched disorder) to use 
   as simulated disorder into our model system.}
@@
 
-  When we allow monomer columns to move independently in the $z$-direction, the
+  However, when we allow monomer columns to move independently in the $z$-direction, the
   intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
-  diffraction patterns smooths out. This is shown by creating a simplified sandwiched
-  configuration, where each head group is represented by a point scatterer,
+  diffraction patterns smooths out. We can demostrate this by creating a simplified sandwiched
+  configuration (simplified in the same way as described above), 
   %simple systems 
@@
   %BJC11: It feels redundant and wordy saying the above rather than simple systems.
-  with varying amounts of association between columns. In the low limit, 
+  with varying amounts of statistical correlation between columns. In the low limit, 
   the center of mass of columns are situated at the same $z$-coordinate. 
@@
   move past each other. When $f = 1$, the columns move independently and the
-  $q_r$ cross-section smooths out (Figure~\ref{fig:column_displacement}). Any
-  amount of dependence results in sharp peaks. The intensity of R-$\pi$ decreases
+  $q_r$ cross-section smooths out completely (Figure~\ref{fig:column_displacement}). Any
+  amount of dependence results in some presence of independent sharp peaks, though significantly attenuated at $f$ nearer 1. The intensity of R-$\pi$ also decreases
   with increasing column independence. We see an 8-fold decrease in the intensity
-  of R-$\pi$ when $f=1$ versus when $f=0$. It is likely that the discrepancy 
-  between the intensity of R-$\pi$ generated from our simulations versus experiment
-  is primarily due to highly correlated, glassy columns in our initial configurations.
-
+  of R-$\pi$ when $f=1$ versus when $f=0$ for our simplified model systems.
+  %MRS12: somewhere will have to talk about stability and relative free energy of the more disordered initial configurations.
+  %MRS12: we MIGHT have to look at more disordered initial configurations.
+I think this can likely be done with just equilibration, where we see how different the quenched disorder when starting from an ensemble of structures, and putting off actually calculating scattring from a large number of simulations.
   \begin{figure}
@@
 
-  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
-  cross-section of R-$\pi$ to, somewhat counterintuitively, to decrease. Using a 
-  %BJC11: ^ Not sure this is counterintuitive to people thinking in reciprocal space.
-  system with uncorrelated columns, we modified the disorder in both the $r$ and
-  $\theta$ directions by multiplying their values by a factor of 0.5 and 2 
-  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
-  by 88\%. When we double the noise, the FWHM decreases by 51\%.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
-  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
-	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
-	  $theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
-	  we double the disorder (Noise factor = 2), the FWHM decreases by
-	  51\%.}\label{fig:qy_fwhm}
-  \end{figure}
-
-  The columns in the atomistic simulated system are highly correlated. If the columns were
+ It therefore seems likely that the discrepancy 
+  between the intensity of R-$\pi$ generated from our simulations versus experiment
+  is primarily due to highly correlated columns in our initial configurations, likely due to the highly symmetric starting configuration. If the columns were
   uncorrelated, $g(z)$ of the ordered sandwiched system would very closely resemble 
@@
 
+  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
+  cross-section of R-$\pi$ to, somewhat counterintuitively, to decrease. Using a 
+  system with uncorrelated columns, we modified the disorder in both the $r$ and
+  $\theta$ directions by multiplying their values by a factor of 0.5 and 2 
+  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
+  by 88\%. When we double the noise, the FWHM decreases by 51\%. %MRS12: is there a structral 
+  %implicatiob to the above?  It should be given explicitly so readers see where it fits in the story .
+  % It could be that there is no real structural implication, which is fine, as long as its explicitly stated. 
+  %is q_r cross-section right in experiment?  Does this explain differences our simulations would need to have?
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
+  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
+	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
+	  $theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
+	  we double the disorder (Noise factor = 2), the FWHM decreases by
+	  51\%.}\label{fig:qy_fwhm}
+  \end{figure}
+
   %BJC9: Note that the magnitude of the correlation function is much lower than 
@@
   between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
-  which is also likely a consequence of highly correlated columns.
-
-  The architecture of each column is likely in between sandwiched and parallel
+  which is also likely a consequence of columns that are too highly correlated.
+
+  The architecture of each column is therefore likely in between sandwiched and parallel
   displaced. The parallel displaced configuration that we have simulated in this
@@
   rearrangements of the system are much longer than what we can feasibly simulate. 
-  As a result, it will be difficult to exactly reproduce the work here, but we are
-  confident that one can draw the same conclusions using our methodology.
+  %MRS12: I don't think this is necessary.  They should reproduce the same findings, if they use a similar quenched configuration. 
+  %As a result, it will be difficult to exactly reproduce the work here, but we are
+  %confident that one can draw the same conclusions using our methodology.
 
@@
   the position of monomers in parallel displaced configurations alternate every other layer, 
-  we know that such a configuration will not produce R-double, but only off-axis 
+  such a configuration will not produce R-double, but only off-axis 
   reflections at the same $q_z$ value~\cite{harburn_atlas_1975}. There is not a unique solution
@@
   We have proposed configurations that result in the appearance of R-double below, and we can 
-  speculate which makes the most physical sense. We show that we cannot achieve a long-term
+  speculate which makes the most physical sense. It appears that we cannot achieve a long-term
   stable system that exhibits R-double without the inclusion of small amounts of water in the pores.
@@
 % BJC6: removed to cut down on amount of material. This one is the biggest stretch in my opinion.
-%  We can produce R-double if our initial configuration contains alternating parallel and
-%  anti-parallel carboxylate groups relative to the plane of the monomer's phenyl ring.
-%  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). It is difficult to physically
-%  justify this system. Systems built this way are only stable if position restraints are placed
-%  on all head group heavy atoms. Carboxylate groups quickly revert to the parallel position as 
-%  restraints are released. There is an appreciable energy barrier that prevents rotation
-%  of carboxylate groups attached to phenyl rings since the group extends the system's 
-%  $\pi$ conjugation (citation) (See Figure S-\ref{S-fig:carboxylate_dihedral_rb}).
+%MRS12: I think it is useful to put in just to show we've been thinking about them.  Can omit the figure in the main text.
+ One way toproduce R-double if our initial configuration contains alternating parallel and
+anti-parallel carboxylate groups relative to the plane of the monomer's phenyl ring.
+%  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). 
+It is difficult to physically justify this system.
+Systems built this way are only stable if position restraints are placed on all head group heavy atoms.
+Carboxylate groups quickly revert to the parallel position as restraints are released.
+There is an appreciable energy barrier that prevents rotation of carboxylate groups attached to phenyl rings since the group extends the system's $\pi$ conjugation (citation) (See Figure S-\ref{S-fig:carboxylate_dihedral_rb}), which is significant even considering possible overestimates of the barrier height in the classial force field.
 %  
@@
 
-%MRS10: I wonder if it would be better to lead with what we think IS the answer, and then rule out other effects.  
-  We can produce R-double if we rotate monomers with respect to vertically adjacent monomers. 
+  One way to could produce R-double if we rotate monomers with respect to vertically adjacent monomers. 
   In this configuration, monomers are rotated so that the vector created by the  
@@
   tails to sit between adjacent monomer tails which may be the most favorable way for them to
-  pack. This configuration is stable short-term while unrestrained however R-double quickly 
-  fades after a few nanoseconds of simulation. 
-  %Still, this may be the most reasonable way for R-double to appear in a dry system. 
-  The long-term stability of a configuration similar to this may be feasible if monomers stay
-  stacked 3.7 \AA~apart.
-
-  We can also produce R-double if layers are not uniformly spaced. Rather,
-  monomers might form pairs that stack less than 3.7~\AA~apart, and whose center
-  of masses are spaced 7.4 \AA~ from the next pair of monomers (Figure
-  ~\ref{fig:staggered_rzplot_norestraints}). To our knowledge, there have been no
-  studies that specifically address the possibility of a configuration like this.
+  pack. This configuration is only stable for a few nanoseconds R-double quickly  fades. 
+  %MRS12: seems like unnecssary speculation below, since there are a lot of cancelling affects. 
+  %The long-term stability of a configuration similar to this may be feasible if monomers stay
+  %stacked 3.7 \AA~apart.
+
+  We can also produce R-double if layers are not uniformly, but instead form pairs that stack less 
+  than 3.7~\AA~apart, with center
+  of masses are spaced 7.4 \AA~ from neighboring pairs of monomers (Figure
+  ~\ref{fig:staggered_rzplot_norestraints}). 
+  %MRS12: not sure this is necessary.
+  %To our knowledge, there have been no
+  %studies that specifically address the possibility of a configuration like this.
   Our force field causes our system to tend towards uniformly spaced layers.
   Simulations of unevenly spaced systems are only stable if position restraints
-  are applied to heavy atoms of the phenyl rings.  There is little evidence from
-  QM studies of stacked $\pi-\pi$ systems that this behavior is
+  are applied to heavy atoms of the phenyl rings.  Additionally, there is little evidence from
+  QM studies of stacked $\pi-\pi$ systems that such uneven stacking could be energetically stable.
   incorrect.~\ref{tauer_beyond_2005}
 
-  Adding water to the system appears to promote the appearance of R-double,
-  through the creation of hydrogen bonding of water to carboxylate groups of
-  consecutive layers. We added water to the parallel displaced and sandwiched
+  However, the addition of water to the system does promote the appearance of R-double.
+%  through the creation of shared hydrogen bonds between water molecules and carboxylate
+%  groups of vertically stacked monomers. 
+  We added water to the parallel displaced and sandwiched
   configurations in the ordered basin and equilibrated them according to the wet
@@
 
-  R-double appears in the solvated system due to the structure of the head
+  R-double appears in the solvated system due to the structuring of the head
   groups. To demonstrate this, we removed the head groups from the trajectory
@@
   with a head group above itself, it will be less likely to share a water molecule 
-  with a head group below it due to steric constraints. The monomer head group below
+  with a head group below it due to geometric constraints. The monomer head group below
   can just as easily share a water molecule with a head group below itself. In this scenario,
@@
   H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity. 
+  Anecdotal evidence from other researchers suggests that membranes are less likely to assemble 
+  under completely dry conditions~\cite{personal_communication_with_mike_mcgrath}, supporting the idea that the ``dry'' structures do absob some water.
   This detail may therefore be important for reproducing the results of Feng et al.

### 2018-08-18 Ben_Manuscripts/structure_paper/Draft.tex
comments.

@@
 %MRS12: I think it is useful to put in just to show we've been thinking about them.  Can omit the figure in the main text.
- One way toproduce R-double if our initial configuration contains alternating parallel and
+ One way to produce R-double if our initial configuration contains alternating parallel and
 anti-parallel carboxylate groups relative to the plane of the monomer's phenyl ring.
@@
   are applied to heavy atoms of the phenyl rings.  Additionally, there is little evidence from
-  QM studies of stacked $\pi-\pi$ systems that such uneven stacking could be energetically stable.
-  incorrect.~\ref{tauer_beyond_2005}
+  QM studies of stacked $\pi-\pi$ systems that such uneven stacking could be energetically stable.~\ref{tauer_beyond_2005}
 
@@
   together in the $z$-direction. Blue monomers were stacked above orange monomers in the
-  initial configuration. (c) We group the $z$-coordinate of the center of mass of monomer
+  initial configuration. 
+  %MRS12: I think subfigure C can be moved to supporting, and we just desribe the alternating structure in the text.
+I think %it's likely to be too confusing for many readers as a figure, and takes up too much space.
+(c) We group the $z$-coordinate of the center of mass of monomer
   head groups into 20 bins. Peaks in the distributions indicate a shared hydrogen bonded
@@
   is separated by twice the average monomer stacking distance, while the four monomers 
-  involved are unequally spaced. These conditions may give rise to R-double.}\label{fig:hbonds}
+  involved are unequally spaced. These conditions seem likely to give rise to R-double.}\label{fig:hbonds}
   \end{figure}

### 2018-08-21 Ben_Manuscripts/structure_paper/Draft.tex
edits in response to comments

@@
 
-  \subsection{Equilibration}
-
+  \subsection{Equilibration}\label{section:equilibration}
   We developed equilibration schemes for creating dry and wet configurations.
@@
 
-  %MRS8: we should ask Matt see if we can give the github repository
-  %for the XRD determination in the paper for reproducibility. I will do that. 
   We generated simulated XRD patterns based on atomic coordinates in order to make
@@
 
-  We normalized all diffraction patterns relative to R-alkanes. We believe that the
-  alkane-alkane density, averaged over all angles, is the feature most likely to be
-  replicated between experiment and simulation, as atomistic alkane parameters are 
-  relatively well studied. Other features are dependent on 
-  system ordering which is likely to have some dependence on initial configuration. 
-  We calculated the average intensity within R-alkanes of the experimental pattern,
-  $I_{avg}$ and divided all intensities by this value. In this way, the average intensity
-  of R-alkanes was equal to 1. When calculating $I_{avg}$, we excluded intensities 
-  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the simulated
-  patterns differ from experiment in those regions in all cases. Specifically, in contrast
-  to the experimental WAXS pattern, R-$\pi$, as it appears in the simulated diffraction 
-  patterns, intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set
-  an upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$. 
-  Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored uniformly. 
-  We applied the same scaling method to the simulated patterns. We carefully chose a scaling
-  factor of $f=3.1$ in order to visibly display all features in all patterns.
+  We normalized all diffraction patterns relative to R-alkanes. We believe that
+  the alkane-alkane density, averaged over all angles, is the feature most likely
+  to be replicated between experiment and simulation, as atomistic alkane
+  parameters are relatively well studied. Other features are dependent on system
+  ordering which is likely to have some dependence on initial configuration.  We
+  calculated the average intensity within R-alkanes of the experimental pattern,
+  $I_{avg}$ and divided all intensities by this value. In this way, the average
+  intensity of R-alkanes was equal to 1. When calculating $I_{avg}$, we excluded
+  intensities within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$,
+  since the simulated patterns differ from experiment in those regions in all
+  cases (See Figure~\ref{fig:ralkanes}). Specifically, in contrast to the
+  experimental WAXS pattern, R-$\pi$, as it appears in the simulated diffraction
+  patterns, intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set an
+  upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$.
+  Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored
+  uniformly.  We applied the same scaling method to the simulated patterns. We
+  carefully chose a scaling factor of $f=3.1$ in order to visibly display all
+  features in all patterns.
+
+%BJC12: redundant -- copied from methods
+%  We developed standardized methods of measuring the intensity of reflections of interest
+%  in the experimental and simulated X-ray diffraction patterns presented in this work. Here,
+%  we graphically illustrate the methods used for measuring these intensities.
+
+%  All diffraction patterns are normalized according to R-alkanes and the intensities
+%  of all reflections are reported relative to the intensity of R-alkanes. The region
+%  used to calculate the average intensity of R-alkanes is shown in
+%  Figure~\ref{fig:ralkanes}. The top region is excluded because, in the simulated
+%  patterns, R-$\pi$ intersects with R-alkanes.
+
+  We reported the intensities of R-$\pi$ and R-double by recording the maximum values
+  of the peaks of the $q_z$ cross-section of the experimental pattern at $q_r=0$ 
+  (Figure~\ref{fig:rpi_rdouble}). In the case of the experimental pattern, the peak
+  heights are not perfectly symmetrical, so we report the average of the two heights.
+
+  We measured the intensity of R-spots by averaging the peak heights produced
+  by radially integrating the patterns within the R-alkanes region
+  (Figure~\ref{fig:rspots}).  In some patterns, the spots are not easily
+  discernable due to obstruction by other features. In that case, we report the
+  average intensity at the intersection of R-alkanes with the $q_z$ value of
+  R-double since that is where we expect it to appear based on experiment. Since
+  R-double does not appear in our simulated patterns, we estimate where it should
+  appear as half of the $q_z$ value of R-$\pi$.
+
+ % We measured the intensity of R-spots by calculating the average intensity
+ % within a region selected by visual inspection. We report the average intensity
+ % within the regions highlighted in red in Figure~\ref{fig:rspots}.
+
+  We measured the intensity of R-pores based on the intensity of the leading peak
+  (closest to $q_r$ = 0) of the $q_r$ cross-section of the patterns at $q_z$=0
+  (Figure~\ref{fig:saxs_xsection}). The beamstop covers most of the small angle
+  reflections in the experimental 2D WAXS pattern. In order to compare the simulated
+  intensity of R-pores to experiment, we used the $q_r$ cross-section of 2D SAXS 
+  which was generated from the same sample. Since the d\textsubscript{110} peak is  %BJC12: verify which crystal plane it is.
+  partially exposed in the experimental 2D WAXS pattern, we normalized the experimental 
+  2D SAXS cross-section by matching the intensity of the d\textsubscript{110} peak 
+  between it and the experimental 2D WAXS cross-section. It is possible that the peak
+  is not fully captured in the 2D WAXS pattern and that our estimate of the intensity
+  of R-pores for the experimental pattern is underestimated.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{ralkanes.png}
+  \caption{R-alkanes}\label{fig:ralkanes}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{rpi_rdouble.png}
+  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{angular_integration.png}
+  \caption{R-spots}\label{fig:rspots}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{saxs_xsection.png}
+  \caption{R-spots}\label{fig:saxs_xsection}
+  \end{subfigure}
+  \caption{(a) We measured the intensity of R-alkanes by calculating the average 
+  intensity within the region bounded by $|\mathbf{q}|$ = 1.4$\AA^{-1}$ and 
+  1.57$\AA^{-1}$ (between 4.0 and 4.5 \AA in real space). We excluded intensities
+  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
+  simulated patterns differ from experiment in those regions in all cases. (b) We
+  measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
+  cross-section of the diffraction pattern. (c) We measured the intensity of R-spots
+  by averaging the peak heights produced by radially integrating the patterns within 
+  the R-alkanes region. We took the intensity of R-spots as the average of the 
+  peak intensities near 37 and 143 $\degree$. (d) We measured the intensity of 
+  R-pores by measuring the height of the leading peak (closest to $q_r$=0) of 
+  the cross-section of the diffraction patterns along the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
+  \end{figure}
 
@@
 
-  We 
-  %MRS12: sounds too much like structure refinement
-  %further refined our structural understanding 
-  can better understand the structure of the system by simulating X-ray 
-  diffraction patterns produced from equilibrated MD trajectories and comparing them
-  to experiment (see section~\ref{method:xrd}). We tested systems built with 5 columns
-  per pore in the parallel displaced and sandwiched configurations at 300 K in the 
-  ordered and disordered basins,
-  %MRS12: added
-  as those were the most consistent with the most unambiguous X-ray diffraction patterns, the pore-to-pore spacing and the stacking distance.
-We generated simulated patterns using the 
-  %MRS12: maybe refer to part of methods where we determined which ones were equilibrated?  Also, maybe say locally equilibrated? Since we know it might be only metastable. 
-equilibrated
-  portion of each simulation trajectory. There are two important factors to take into
-  account when looking at differences between experimental XRD and simulated XRD. First,
-  the simulated diffraction patterns have some noise, especially along the $q_z$ axis 
-  at $q_r$=0, which is where several of the more interesting features are located. This
-  is due to the angle averaging of the 3D structure factor around the $q_z$-axis, meaning
-  there are fewer samples as  $q_r$ approaches 0. The amount of samples 
-  %MRS12: added
-  required to
-  to converge along
-  the $q_z$ axis is analyzed in Supporting Information section S-\ref{S-section:xrd_noise}. 
-  More importantly, our simulations do not appear to be long enough to sample truly 
+  We can better understand the structure of the system by simulating X-ray
+  diffraction patterns produced from equilibrated MD trajectories and comparing
+  them to experiment (see section~\ref{method:xrd}). We tested systems built with
+  5 columns per pore in the parallel displaced and sandwiched configurations at
+  300 K in the ordered and disordered basins, as those were the most consistent
+  with the most unambiguous X-ray diffraction features, the pore-to-pore spacing
+  and the stacking distance.  We generated simulated patterns using the locally
+  equilibrated portion of each simulation trajectory (See
+  Section~\ref{method:equil_time}. There are two important factors to take into
+  account when looking at differences between experimental XRD and simulated XRD.
+  First, the simulated diffraction patterns have some noise, especially along the
+  $q_z$ axis at $q_r$=0, which is where several of the more interesting features
+  are located. This is due to the angle averaging of the 3D structure factor
+  around the $q_z$-axis, meaning there are fewer samples as  $q_r$ approaches 0.
+  The amount of samples required to to converge along the $q_z$ axis is analyzed
+  in Supporting Information section S-\ref{S-section:xrd_noise}.  More
+  importantly, our simulations do not appear to be long enough to sample truly
   independent configurations within their respective metastable basins (see
-  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting the
-  results of the XRD. The simulated patterns generated for all systems studied are shown
-  and compared to experiment in Figure~\ref{fig:XRDsim}.
-
-  %MRS11: the fact that they are not within their metastable basis DOESN'T just affect the noise it affects everything else.
-If we had 100 times longer, it would reduce the noise along the z axis a lot, but the peaks would likely still be too intense, as we would have a lot of data long the z, but still be in the timescales that are too slow to reduce the peak intensity.
-Did a pass above.
+  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting
+  the results of the XRD. The simulated patterns generated for all systems
+  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
 
@@
 	\end{subfigure}	
-	\caption{Simulated XRD patterns show some qualitative agreement with experiment. Shown is a 
-	comparison of the (a) Sandwiched, ordered basin (b) Sandwiched,
-	disordered basin (d) Parallel displaced, ordered basin and (e) Parallel displaced, disordered basin 
-	configurations with (c) experimental WAXS. 	In all cases, R-pores, R-alkanes and R-$\pi$ are 
-	present to some degree. R-spots is also present, however it is generally partially covered by the
-	broad R-$\pi$ reflection. Quantitative comparisons of the relative intensities of reflections of
-	interest are presented in Table~\ref{table:relative_intensities_300K}. In both XRD patterns generated
-	from parallel displaced patterns, there is a faint line across $q_z \sim 0.7~$\AA$^{-1}$, half
-	the simulated value of R-$\pi$. Although it does not cross through $q_r = 0$~\AA$^{-1}$, it is at 
-	the same $q_z$ value where we expect R-double to be present. Still, R-double is not fully reproduced
+	\caption{Simulated XRD patterns show some qualitative agreement with
+		experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b)
+		Sandwiched, disordered basin (d) Parallel displaced, ordered basin and (e)
+		Parallel displaced, disordered basin configurations with (c) experimental WAXS.
+		The major reflections of interest (See Figure~\ref{fig:SWAXS} for their
+		definitions) are present at varying degrees. In all cases, R-pores, R-alkanes
+		and R-$\pi$ are present to some degree. R-spots is also present, however it is
+		generally partially covered by the broad R-$\pi$ reflection. Quantitative
+		comparisons of the relative intensities and locations of reflections of
+		interest are presented in Table~\ref{table:relative_intensities_300K}. In both
+		XRD patterns generated from parallel displaced patterns, there is a faint line
+		across $q_z \sim 0.7~$\AA$^{-1}$, half the simulated value of R-$\pi$. Although
+		it does not cross through $q_r = 0$~\AA$^{-1}$, it is at the same $q_z$ value
+		where we expect R-double to be present. Still, R-double is not fully reproduced
 		in any of the simulated patterns.}~\label{fig:XRDsim} 
-        %MRS12: I would repeat the labels from figure 3.  Minimum, need to refer back to that figure so they know where to find the definitions of the lables. 
   \end{figure}
@@
   Table~\ref{table:relative_intensities_300K}. Our approach for measuring the intensity of
-  each reflection are described in section S-\ref{S-section:xrd_intensities}. %MRS12: should that be in Methods instead of suporting?  Not sure.
+  each reflection are described in section S-\ref{S-section:xrd_intensities}. 
+  %MRS12: should that be in Methods instead of suporting?  Not sure.
+  %BJC12: moved into methods for now.
 
@@
   %MRS12: question: is the normalization for the simulated systems the same, no matter if disordered, etc.  If not chosen to be exactly the same, how different are they?
-  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
-  intensity of R-alkanes in each pattern equals 1, show R-$\pi$ reflections that are significantly higher 
-  than experiment and R-spots reflections that are slightly lower than experiment. R-double
-  does not appear in any simulated patterns, and thus has no measurable intensity.}
+  %BJC12: Are you asking what the normalization constant is that I divide the patterns by for each system? I'll have to check. 
+  \caption{The simulated XRD patterns of the systems tested, normalized so that
+	  the average intensity of R-alkanes in each pattern equals 1, show R-pores and
+	  R-$\pi$ reflections that are significantly higher than experiment and R-spots
+	  reflections that are slightly lower than experiment. R-double does not appear
+	  in any simulated patterns, and thus has no measurable intensity.}
   \label{table:relative_intensities_300K} 
@@
 
-  We normalized the experimental and simulated diffraction patterns so that the average
-  intensity within R-alkanes is equal to 1 because we believe that R-alkanes is the
-  experimental feature most likely to be reproduced by our simulations. 
-  %BJC11: could add some support of this statement - perhaps a reference to the original
-  % GAFF forcefield paper? Need to actually check it though.
-  %MRS12: first pass.  
-  We reach this conclusion because alkane
-  parameters in GAFF and AMBER forcefields are generally reproduce data well.~\cite{original_gaff_paper} 
+  We normalized the experimental and simulated diffraction patterns so that the
+  average intensity within R-alkanes is equal to 1 because we believe that
+  R-alkanes is the experimental feature most likely to be reproduced by our
+  simulations.  We reach this conclusion because alkane parameters in GAFF and
+  AMBER forcefields generally reproduce data well.~\cite{original_gaff_paper} 
   %MRS12: Citation is: https://doi.org/10.1002/jcc.20035  could also cite: https://pubs.acs.org/doi/pdf/10.1021/ct200731v
+
   %MRS12: below - say what appears close means?  radius of max is X vs Y.
-  R-alkanes appears close to its expected location. In all cases, the maximum intensity
-  of R-alkanes appears at a $|\mathbf{q}|$ value only slightly higher than experiment. 
+  R-alkanes appears close to its expected location. In all cases, the maximum
+  intensity of R-alkanes along the $q_r$ axis at $q_z$=0, which we use to
+  estimate its location, appears at a $|\mathbf{q}|$ value that is, at most,
+  3.5\% higher than higher than experiment. 
   %MRS12: different pass?
@@
 Could still good languange if the conclusion was that the binning error was similar in size to errors in the location R-alkane.
-  The error in the simulated diffraction patterns is less that the error due binning in eack frequency direction, so was not further investigated. 
+  %BJC12: I use the maximum intensity of R-alkanes along the q_r axis at qz=0 to determine its location.
+  The error in the simulated diffraction patterns is less that the error due
+  binning in each frequency direction, so was not further investigated. 
   %We expect that the exact location of R-alkanes will not be perfect in our simulations
@@
 
-  R-pores is about 4 times more intense than experiment in all simulated systems. We
-  hypothesize that this is primarily due to the relatively perfect infinite hexagonal
-  array of pores in the simulated systems. In the real system, periodicity of the 
-  hexagonal array is disrupted by misalignment of the crystalline domains and the
-  pore-to-pore distances fluctuate more over long time scales. 
+  R-pores is about 4 times more intense than experiment in all simulated
+  systems. We hypothesize that this is primarily due to the relatively perfect
+  infinite hexagonal array of pores in the simulated systems. In the real system,
+  periodicity of the hexagonal array is disrupted by misalignment of the
+  crystalline domains and the pore-to-pore distances fluctuate more over long
+  time scales. 
   % BJC11: Using simple systems, I can show that more highly fluctutating pore-to-pore
@@
   % MRS12:  Agreed. Rephrased a bit.
-  The agreement in intensity in R-pores obtained here is sufficient for this study because this intensity is primarily controlled by longer-range organization that cannot be captured by simulation of only 4 pores and because we are concered with the with the structure of the individual pores themselves.
-
-  The location of the leading peak of R-pores is directly related to the average 
-  distance between pores. However, there is substatial uncertainty in the exact location 
-  relative to the bin size used for the Fourier space transformation. We can instead 
-  measure the average distance between columns
-  with more precision in real space (See Section~\ref{method:pore_spacing}). We showed
-  that we achieve experimentally consistent pore spacings in our simulations in 
-  Section~\ref{section:section:mon_per_pore}.
+  The agreement in intensity in R-pores obtained here is sufficient for this
+  study because this intensity is primarily controlled by longer-range
+  organization that cannot be captured by simulation of only 4 pores and because
+  we are only concerned with the structure of the individual pores themselves.
+
+  The location of the leading peak of R-pores is directly related to the
+  average distance between pores. However, there is substantial uncertainty in
+  the exact location relative to the bin size used for the Fourier space
+  transformation. We can instead measure the average distance between columns
+  with more precision in real space (See Section~\ref{method:pore_spacing}). We
+  showed that we achieve experimentally consistent pore spacings in our
+  simulations in Section~\ref{section:section:mon_per_pore}.
 
@@
 
-  The intensity of R-spots is close to experiment when generated from any of our
-  simulated systems. 
-  Because the R-spots reflection is difficult to distinguish visually as it appears 
-  at the same $|\mathbf{q}|$ as R-alkanes, we calculate 
-  the intensity of R-spots by assuming that its $q_z$ location should be roughly in line with 
-  the experimental R-double, half the $q_z$ distance of R-$\pi$).
-  %The appearance of R-spots is inconspicuous in most cases so we
-  %assumed that the location of R-spots, in terms of $|\mathbf{q}|$ would coincide with
-  %that of R-alkanes, and that it's $q_z$ location should be roughly in line with 
-  %R-double (half the $q_z$ location of R-$\pi$) as it appears in the experimental pattern.
-  We measured the intensity of R-spots by radially integrating the simulated
-  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$ (between
-  4 and 4.5 $\AA$ in real space) and then locating and recording the intensity of the 
-  appropriate peaks in the resulting distribution.
+  The intensity of R-spots is close to experiment when generated from any of
+  our simulated systems. We measured the intensity of R-spots by radially integrating the simulated
+  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$
+  (between 4 and 4.5 $\AA$ in real space) and then locating and recording the
+  intensity of the appropriate peaks in the resulting distribution. Because the
+  R-spots reflection is difficult to distinguish visually as it appears at the
+  same $|\mathbf{q}|$ as R-alkanes, we calculate the intensity of R-spots by
+  assuming that its $q_z$ location should be roughly in line with the
+  experimental R-double, half the $q_z$ distance of R-$\pi$).
 
@@
   %R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
-  Previous literature has attributed the R-spots reflection in this particular WAXS dataset as 
-  the result of tilted alkane chains~\cite{feng_scalable_2014}. 
-  %Here we refute that explanation and show that the 
-  We measured the tilt angle of the alkane chains of
-  the 280K system and found that it equilibrates to an average tilt angle of
+  Previous literature has attributed the R-spots reflection in this particular
+  WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
+  We measured the tilt angle of the alkane chains of the 280K system and found
+  that it equilibrates to an average tilt angle of
   -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
-  used to explain R-spots. Similar lack of more than a statistically negligible tilt occured when 
-  we performed the simulations with a number of other starting configurations, obtaining similar results.%MRS12: I know we discussed this earlier; there were a number of things that were done to verify this results was consistent, and I think that a rief summary would help.
-
-  In order to more clearly identify the structural reasons for R-spots, we equilibrated an ordered basin sandwiched 
-  configuration at 280K to moderately increase the order and therefore intensity. 
-  Many force fields do not obtain the correct equilibrium structure
-  at precisely the experimental temperature. Wang et al. highlighted the shortcoming of 
-  some of the most popular protein force field in predicting the temperature dependence 
-  of protein structural ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
-  our membrane system, simulated at 300K, is under-structured in the tail region compared
-  to the experimental structure at 300K. We found that lowering the temperature indeed better 
-  resolved R-spots (Figure~\ref{fig:sandwiched280K}), suggesting that our 'effective' 
-  temperature might indeed be too high, understabilizing structure.
-
-  The Evidence from the simulations strongly suggests that the R-spots signal
- is not a 
-  result of alkane chain tilt.
+  used to explain R-spots. Even when we placed position restraints on the
+  monomers in a tilted initial configuration, monomers quickly reduced their tilt
+  relative to the $xy$ plane to an angle statisically neglibible from zero. (See 
+  Section S-TBD). 
+  %Similar lack of more than a statistically negligible
+  %tilt occured when we performed the simulations with a number of other starting
+  %configurations, obtaining similar results. 
+  %MRS12: I know we discussed this earlier; there were a number of things that were done to verify this results was consistent, and I think that a rief summary would help. 
+  %BJC12: It was primarily us trying to induce tilt by equilibrating with position restraints. I'm trying to think of what else we might have done. I changed the last sentence for now
+
+  In order to more clearly identify the structural reasons for R-spots, we
+  equilibrated an ordered basin sandwiched configuration at 280K to moderately
+  increase the order and therefore intensity.  Many force fields do not obtain
+  the correct equilibrium structure at precisely the experimental temperature.
+  Wang et al. highlighted the shortcoming of some of the most popular protein
+  force field in predicting the temperature dependence of protein structural
+  ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
+  our membrane system, simulated at 300K, is under-structured in the tail region
+  compared to the experimental structure at 300K. We found that lowering the
+  temperature indeed better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
+  suggesting that our 'effective' temperature might indeed be too high,
+  understabilizing structure.
+
+%  The Evidence from the simulations strongly suggests that the R-spots signal
+% is not a 
+%  result of alkane chain tilt.
 
@@
   of a simple hexagonal array constructed based on the peak angles in
-  Figure~\ref{fig:layered_tails} shows reflections in the same locations as R-spots,
-  in addition to vertical stacking reflections along the $q_z$ axis that would 
-  intersect with R-$\pi$ (Figure~\ref{fig:hexagonal_ft}).
+  Figure~\ref{fig:layered_tails} shows reflections in the same locations as
+  R-spots, in addition to vertical stacking reflections along the $q_z$ axis that
+  would intersect with R-$\pi$ (Figure~\ref{fig:hexagonal_ft}).
 
@@
 
-  The position, shape and intensity of R-$\pi$, generated from simulations at 300K, are 
-  qualitatively similar to experiment, but have significant quantitative differences. The reflections appear
-  at lower $q_z$ values, they are more intense, and the shape of its cross-sections, 
-  especially in the $q_r$ direction are different relative to the experimental system.
-  For comparison, see Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the simulated
-  XRD generated from the ordered parallel displaced configuration as an example. In 
-  this section, we explore the various contributions to these discrepancies, and use this information to 
-  speculate on what reasonable differences in the simulations could explain the discrepancies.
+  The position, shape and intensity of R-$\pi$, generated from simulations at
+%  300K, are qualitatively similar to experiment, but have significant
+%  quantitative differences. 
+% BJC12: I don't think I agree that they are qualitatively similar either. The
+% simulated qr cross-sections are spikey and too low (which is qualitatively
+% evident when you look at the simulated XRD patterns)
+  300K have qualitative and quantitative differences from experiment.
+  The reflections appear at lower $q_z$ values, they
+  are more intense, and the shape of its cross-sections, especially in the $q_r$
+  direction are different relative to the experimental system.  For comparison,
+  see Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the
+  simulated XRD generated from the ordered parallel displaced configuration as an
+  example. In this section, we explore the various contributions to these
+  discrepancies, and use this information to speculate on what reasonable
+  differences in the simulations could explain the discrepancies.
 
@@
 %  groups within the same column. 
-  The resulting distributions are generally characterized
-  by decaying oscillatory behavior where the average distance between peaks corresponds
-  to the average distance between stacked monomer head groups (Figure~\ref{fig:correlation}).
-  We calculated this equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between
-  monomers using Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked
-  monomers is greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
-  basins at the high part of that range and are on average 0.2 and 0.3 \AA~more distant. This behavior is
+  The resulting distributions are generally characterized by decaying
+  oscillatory behavior where the average distance between peaks corresponds to
+  the average distance between stacked monomer head groups
+  (Figure~\ref{fig:correlation}).  We calculated this equilibrated vertical
+  stacking distance, $\mathit{d}_{equil}$, between monomers using
+  Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked monomers is
+  greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
+  basins at the high part of that range and are on average 0.2 and 0.3 \AA~more
+  distant. This behavior is
   not surprising since GAFF models atoms as point charges and  % BJC11: need reference %MRS12: just cite the GAFF paper.
-  does not appropriately model the aromatic $\pi-\pi$ interactions, which make it
-  more energetically favorable for the monomers to stack closer together. 
-  It is also possible that the tails prevent close stacking of monomer head groups and we do
-  not achieve the timescales necessary for them to rearrange into a necessarily more
-  tightly packed configuration. However, we equilibrated the system at 500K then annealed it to 300K
-  in an attempt to coerce the tails into a more tightly packed configuration, however 
-  we saw no improvement in packing distance over our 300K models. See section S-TBD for details.
+  does not appropriately model the aromatic $\pi-\pi$ interactions, which make
+  it more energetically favorable for the monomers to stack closer together.  It
+  is also possible that the tails prevent close stacking of monomer head groups
+  and we do not achieve the timescales necessary for them to rearrange into a
+  necessarily more tightly packed configuration. However, we equilibrated the
+  system at 500K then annealed it to 300K in an attempt to coerce the tails into
+  a more tightly packed configuration, however we saw no improvement in packing
+  distance over our 300K models. See section S-TBD for details.
 
@@
   system may be necessary to fully capture the correlation function. We therefore
-  equilibrated a sandwiched system with twice as many monomers per column 
-  so that the system size doubled in the $z$-direction. The correlation length 
-  increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
+  equilibrated a sandwiched system with twice as many monomers per column so that
+  the system size doubled in the $z$-direction. The correlation length increases
+  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
   correlation functions are nearly identical and oscillatory behavior persists
-  throughout $g(z)$ in both cases (See Figure~S-\ref{S-fig:z_correlation_overlay}).
-
-  The broadening of the $q_z$ cross-section of R-$\pi$ is related to $z$-directional
-  correlation between scatters within monomer columns. The correlation length varies as the
-  inverse of the full width at half maximum (FWHM) of the $q_z$ cross-section of R-$\pi$.
-  Using this technique, we calculated the correlation length of the experimental system
-  to be 9.0 \AA. As scatterers become less correlated, we expect that R-$\pi$ will broaden.
-
-  The correlation lengths of vertically stacked scatterers in our atomistic simulations
-  are in reasonable agreement with experiment. Since it is not feasible for us to
-  simulate membranes with much taller columns in order to obtain increased $q_z$ resolution of our
-  simulated XRD patterns, and because the simulated peak shape is convoluted by the
-  extremely intense maximum of R-$\pi$, we measured correlation length by fitting
+  throughout $g(z)$ in both cases (See
+  Figure~S-\ref{S-fig:z_correlation_overlay}).
+
+  The broadening of the $q_z$ cross-section of R-$\pi$ is related to
+  $z$-directional correlation between scatters within monomer columns. The
+  correlation length varies as the inverse of the full width at half maximum
+  (FWHM) of the $q_z$ cross-section of R-$\pi$.  Using this technique, we
+  calculated the correlation length of the experimental system to be 9.0 \AA. As
+  scatterers become less correlated, we expect that R-$\pi$ will broaden.
+
+  The correlation lengths of vertically stacked scatterers in our atomistic
+  simulations are in reasonable agreement with experiment. Since it is not
+  feasible for us to simulate membranes with much taller columns in order to
+  obtain increased $q_z$ resolution of our simulated XRD patterns, and because
+  the simulated peak shape is convoluted by the extremely intense maximum of
+  R-$\pi$, we measured correlation length by fitting
   Equation~\ref{eqn:decaying_exponential} to the peaks of $g(z)$. The correlation
-  length of the parallel displaced, ordered basin system shows the closest agreement
-  with experiment (Table~\ref{table:correlation_length}). 
+  length of the parallel displaced, ordered basin system shows the closest
+  agreement with experiment (Table~\ref{table:correlation_length}). 
   %BJC11: below might confuse the reader
@@
 %  XRD resolution.
-   We could not extract a reliable correlation
-  length from the disordered parallel displaced configuration since the peaks do not show
-  clear patterns that can easily be fit to an exponential decay. The correlation length
-  of both sandwiched systems are relatively low because the height of the first peak of 
+  We could not extract a reliable correlation length from the disordered
+  parallel displaced configuration since the peaks do not show clear patterns
+  that can easily be fit to an exponential decay. The correlation length of both
+  sandwiched systems are relatively low because the height of the first peak of
   $g(z)$ is so high.
@@
   % could say "distance covariance"
-  Overall, we believe our simulations exhibit a realistic amount of distance correlation in the direction parallel to the pore axis between head groups within each column.
-The difference in the FWHM of the $q_z$
-  cross-section of R-$\pi$ between experiment and simulation is less than one bin size
+  Overall, we believe our simulations exhibit a realistic amount of distance
+  correlation in the direction parallel to the pore axis between head groups
+  within each column. The difference in the FWHM of the $q_z$ cross-section of
+  R-$\pi$ between experiment and simulation is less than one bin size
   (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). The more
-  signficant difference between the two cross-sections is their maximum intensity which
-  we study in more detail below.
+  signficant difference between the two cross-sections is their maximum intensity
+  which we study in more detail below.
 
@@
 
-  An exact quantitative comparison between the intensity and FWHM of the experimental
-  and simulated cross-sections of R-$\pi$ is not feasible
-  for several reasons. Experimental peaks broaden due to effects that we can not 
-  easily simulate such as finite size crystalline domains and instrumental resolution.
-  In our simulated XRD patterns, the system size imposes limitations on the resolution,
-  which makes it difficult to reliably fit peaks. This is especially problematic when
-  comparing the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental 
-  FWHM (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
-  Additionally, we model each atom with a Gaussian sphere of electron density, which is a simplification. 
-  However, we can explore reasons for which differences in the simulation structure could change
-  the peak shapes and intensities to be in better agreement with experiment.
+  An exact quantitative comparison between the intensity and FWHM of the
+  experimental and simulated cross-sections of R-$\pi$ is not feasible for
+  several reasons. Experimental peaks broaden due to effects that we can not
+  easily simulate such as finite size crystalline domains and instrumental % reference needed
+  resolution.  In our simulated XRD patterns, the system size imposes limitations
+  on the resolution, which makes it difficult to reliably fit peaks. This is
+  especially problematic when comparing the FWHM of the $q_z$ cross-section of
+  R-$\pi$, where the experimental FWHM (0.11 $\AA^{-1}$) is similar to the bin
+  size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).  Additionally, we model each
+  atom with a Gaussian sphere of electron density, which is a simplification.
+  However, we can explore reasons for which differences in the simulation
+  structure could change the peak shapes and intensities to be in better
+  agreement with experiment.
 
@@
 
-  We studied the shape and intensity of R-$\pi$ by setting up simplified systems
-  where we represent monomer head groups as point scatterers, as described in 
-  Section~\ref{method:simple_systems}. The amount of quenched and thermal disorder
-  present in the atomistic system, which we applied to the simplified systems, are
-  given in Table~\ref{table:quenched_disorder}. The quenched disorder, the deviation of monomers from idealized 
-  symmetric configurations, several times greater than thermal disorder, the deviations of the monomers during the production simulations.
+  We studied the shape and intensity of R-$\pi$ by setting up simplified
+  systems where we represent monomer head groups as point scatterers, as
+  described in Section~\ref{method:simple_systems}. The amount of quenched and
+  thermal disorder present in the atomistic system, which we applied to the
+  simplified systems, are given in Table~\ref{table:quenched_disorder}. The
+  quenched disorder, the deviation of monomers from idealized symmetric
+  configurations, is several times greater than thermal disorder, the 
+  deviations of the monomers from their average positions during the 
+  production simulations. We hypothesize that the quenched disorder is the 
+  same as thermal disorder, but we cannot reach the necssary transition
+  timescales.  
   %MRS12: when reworking the first part of the simulation, our hypothesis for the REASONS behind the quenched disorder will ahave to be addressed.
@@
 It PROBABLY should go before here, when it's first described.
+  %BJC12: I first describe in methods, which seems the wrong place to put that hypothesis, so I tacked it on here.
 
@@
 
-  However, when we allow monomer columns to move independently in the $z$-direction, the
-  intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
-  diffraction patterns smooths out. We can demostrate this by creating a simplified sandwiched
-  configuration (simplified in the same way as described above), 
+  However, when we allow monomer columns to move independently in the
+  $z$-direction, the intensity of R-$\pi$ drops and the $q_r$ cross-section of
+  the simulated diffraction patterns smooths out. We can demostrate this by
+  creating a simplified sandwiched configuration (simplified in the same way as
+  described above), 
   %simple systems 
@@
   %BJC11: It feels redundant and wordy saying the above rather than simple systems.
-  with varying amounts of statistical correlation between columns. In the low limit, 
-  the center of mass of columns are situated at the same $z$-coordinate. 
-  We allow increasing independence of columns by randomly shifting each column
-  in the $z$-direction according to a uniform distribution bounded by (0, 
-  $f \times \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We limit 
-  this discussion to the sandwiched configuration since it is not feasible for
-  columns in the parallel displaced configuration, as we have set them up, to
-  move past each other. When $f = 1$, the columns move independently and the
-  $q_r$ cross-section smooths out completely (Figure~\ref{fig:column_displacement}). Any
-  amount of dependence results in some presence of independent sharp peaks, though significantly attenuated at $f$ nearer 1. The intensity of R-$\pi$ also decreases
-  with increasing column independence. We see an 8-fold decrease in the intensity
-  of R-$\pi$ when $f=1$ versus when $f=0$ for our simplified model systems.
+  with varying amounts of statistical correlation between columns. In the low
+  limit, the center of mass of columns are situated at the same $z$-coordinate.
+  We allow increasing independence of columns by randomly shifting each column in
+  the $z$-direction according to a uniform distribution bounded by (0, $f \times
+  \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We limit this discussion
+  to the sandwiched configuration since it is not feasible for columns in the
+  parallel displaced configuration, as we have set them up, to move past each
+  other. When $f = 1$, the columns move independently and the $q_r$ cross-section
+  smooths out completely (Figure~\ref{fig:column_displacement}). Any amount of
+  dependence results in some presence of independent sharp peaks, though
+  significantly attenuated at $f$ nearer 1. The intensity of R-$\pi$ also
+  decreases with increasing column independence. We see an 8-fold decrease in the
+  intensity of R-$\pi$ when $f=1$ versus when $f=0$ for our simplified model
+  systems.
   %MRS12: somewhere will have to talk about stability and relative free energy of the more disordered initial configurations.
@@
 
- It therefore seems likely that the discrepancy 
-  between the intensity of R-$\pi$ generated from our simulations versus experiment
-  is primarily due to highly correlated columns in our initial configurations, likely due to the highly symmetric starting configuration. If the columns were
-  uncorrelated, $g(z)$ of the ordered sandwiched system would very closely resemble 
+  It therefore seems likely that the discrepancy between the intensity of
+  R-$\pi$ generated from our simulations versus experiment is primarily due to
+  highly correlated columns in our initial configurations, likely due to the
+  highly symmetric starting configuration. If the columns were uncorrelated,
+  $g(z)$ of the ordered sandwiched system would very closely resemble
   Figure~\ref{fig:z_correlation_sandwich} when we average all $z$-slices of the
-  3D correlation function. When we include all $z$-slices in $g(z)$ for our system,
-  the function shows oscillatory behavior and the correlation length nearly triples
-  to 12.4 $\pm$ 0.7 \AA. (Figure~\ref{fig:z_correlation_fullbox}). Since all 
-  columns in our initial configuration are started at the same $z$-coordinate, 
-  $g(z)$ on average exhibits correlation of head groups with other head groups
-  within the same column, with head groups in other columns within the same pore, 
-  and with head groups in different pores.
+  3D correlation function. When we include all $z$-slices in $g(z)$ for our
+  system, the function shows oscillatory behavior and the correlation length
+  nearly triples to 12.4 $\pm$ 0.7 \AA. (Figure~\ref{fig:z_correlation_fullbox}).
+  Since all columns in our initial configuration are started at the same
+  $z$-coordinate, $g(z)$ on average exhibits correlation of head groups with
+  other head groups within the same column, with head groups in other columns
+  within the same pore, and with head groups in different pores.
 
   Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
-  cross-section of R-$\pi$ to, somewhat counterintuitively, to decrease. Using a 
+  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a 
   system with uncorrelated columns, we modified the disorder in both the $r$ and
@@
   (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
-  by 88\%. When we double the noise, the FWHM decreases by 51\%. %MRS12: is there a structral 
+  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
+  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees
+  well with experiment, meaning the quenched configuration contains about the
+  right amount of disorder on the $xy$ plane. However, the relatively low quality
+  of the fit implies that the FWHM may be incorrect, and that the radial ordering
+  of the head groups may need improvement.
+  %MRS12: is there a structral 
   %implicatiob to the above?  It should be given explicitly so readers see where it fits in the story .
@@
   %is q_r cross-section right in experiment?  Does this explain differences our simulations would need to have? 
+  %BJC12: There are structural implications - namely that if the pore region had 
+  % more disordered head groups, then R-pi would sharp. If they were more ordered, it
+  % would get wider. But our fits show similar FWHMs. Even though the fit isn't 
+  % great, I don't think we can say one way or the other. But once we fix everything
+  % else, maybe that's something we could look at.
 
@@
 %  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). 
-It is difficult to physically justify this system.
-Systems built this way are only stable if position restraints are placed on all head group heavy atoms.
-Carboxylate groups quickly revert to the parallel position as restraints are released.
-There is an appreciable energy barrier that prevents rotation of carboxylate groups attached to phenyl rings since the group extends the system's $\pi$ conjugation (citation) (See Figure S-\ref{S-fig:carboxylate_dihedral_rb}), which is significant even considering possible overestimates of the barrier height in the classial force field.
+It is difficult to physically justify this system. Systems built this way are
+only stable if position restraints are placed on all head group heavy atoms.
+Carboxylate groups quickly revert to the parallel position as restraints are
+released. There is an appreciable energy barrier that prevents rotation of
+carboxylate groups attached to phenyl rings since the group extends the
+system's $\pi$ conjugation (citation) (See Figure
+S-\ref{S-fig:carboxylate_dihedral_rb}), which is significant even considering
+possible overestimates of the barrier height in the classial force field. 
 %  
@@
 
-  We can also produce R-double if layers are not uniformly, but instead form pairs that stack less 
-  than 3.7~\AA~apart, with center
-  of masses are spaced 7.4 \AA~ from neighboring pairs of monomers (Figure
+  We can also produce R-double if layers are not uniformly, but instead form
+  pairs that stack less than 3.7~\AA~apart, with center of masses are spaced 7.4
+  \AA~ from neighboring pairs of monomers (Figure
   ~\ref{fig:staggered_rzplot_norestraints}). 
@@
   Simulations of unevenly spaced systems are only stable if position restraints
-  are applied to heavy atoms of the phenyl rings.  Additionally, there is little evidence from
-  QM studies of stacked $\pi-\pi$ systems that such uneven stacking could be energetically stable.~\ref{tauer_beyond_2005}
+  are applied to heavy atoms of the phenyl rings.  Additionally, there is little
+  evidence from QM studies of stacked $\pi-\pi$ systems that such uneven stacking
+  could be energetically stable.~\ref{tauer_beyond_2005}
 
@@
 %  groups of vertically stacked monomers. 
-  We added water to the parallel displaced and sandwiched
-  configurations in the ordered basin and equilibrated them according to the wet
-  equilibration procedure. There is no experimental measurement of water
-  concentration in these membranes so we tested a range of water concentrations
-  from 1\% to 5\%. R-double appears transiently in the simulated XRD pattern of
-  the parallel displaced configuration with 1 wt\% water (Figure
+  We added water to the parallel displaced and sandwiched configurations in the
+  ordered basin and equilibrated them according to the wet equilibration
+  procedure. There is no experimental measurement of water concentration in these
+  membranes so we tested a range of water concentrations from 1\% to 5\%.
+  R-double appears transiently in the simulated XRD pattern of the parallel
+  displaced configuration with 1 wt\% water (Figure
   \ref{fig:solvated_pore_rzplot_norestraints}). It is not initially present, but
@@
 
-  Of all the configurations tested, it is most likely that R-double is induced by water
-  molecules as described above since it is the only mechanism that can be observed without
-  position restraints. The extent of the hydrogen bonding network that forms is largely 
-  determined by the accuracy of the forcefield. It is possible that a more realistic force
-  field would make the effect stronger or weaker. If this is truly the mechanism, it implies
-  that the system studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} was not 
-  truly a thermotropic Col\textsubscript{h} phase. Rather, they were very low water content
-  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity. 
-  Anecdotal evidence from other researchers suggests that membranes are less likely to assemble 
-  under completely dry conditions~\cite{personal_communication_with_mike_mcgrath}, supporting the idea that the ``dry'' structures do absob some water.
-  This detail may therefore be important for reproducing the results of Feng et al.
+  Of all the configurations tested, it is most likely that R-double is induced
+  by water molecules as described above since it is the only mechanism that can
+  be observed without position restraints. The extent of the hydrogen bonding
+  network that forms is largely determined by the accuracy of the forcefield. It
+  is possible that a more realistic force field would make the effect stronger or
+  weaker. If this is truly the mechanism, it implies that the system studied by
+  Feng et al.\cite{feng_scalable_2014,feng_thin_2016} was not truly a
+  thermotropic Col\textsubscript{h} phase. Rather, they were very low water
+  content H\textsubscript{II} phases unintentionally created due to the neat
+  monomers' hydroscopicity.  Anecdotal evidence from other researchers suggests
+  that membranes are less likely to assemble under completely dry
+  conditions~\cite{personal_communication_with_mike_mcgrath}, supporting the idea
+  that the ``dry'' structures do absorb some water.  This detail may therefore be
+  important for reproducing the results of Feng et al.
 
@@
   also periodicity every 8.3 $\AA$, twice the $\pi$-stacking distance, as indicated by the
-  intensity at 0.76 $\AA^{-1}$). In this case, the center of mass of two adjacent pairs 
+  intensity at 0.76 $\AA^{-1}$. In this case, the center of mass of two adjacent pairs 
   is separated by twice the average monomer stacking distance, while the four monomers 

### 2018-08-21 Ben_Manuscripts/structure_paper/Draft.tex
Edits after full read-through

@@
 
-  The H\textsubscript{II} phase pore geometry has a higher theoretical capacity
-  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
-  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
-  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
-  water, neat monomer will form the same hexagonal columnar structure which, in
-  literature, has been referred to as the Col\textsubscript{h} thermotropic
+  The H\textsubscript{II} phase pore geometry (Figure~\ref{fig:assembly}) has a
+  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
+  The H\textsubscript{II} phase forms at room temperature in the presence of
+  c.a.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
+  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
+  form the same hexagonal columnar structure which, in literature, has been
+  referred to as the Col\textsubscript{h} thermotropic
   phase\cite{feng_scalable_2014}. 
@@
 %  since it encodes all structural details down to the sub-nm scale.  
-  There are five major features of interest present in the 2D experimental pattern shown 
-  in Figure \ref{fig:WAXS}.
+  There are five major features of interest present in the 2D experimental
+  pattern shown in Figure~\ref{fig:WAXS}.
 
@@
 	space periodicity of 7.4 \AA. Since this reflection corresponds to double
-	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
+	the spacing of R-$\pi$ in real space, we will refer to it as R-double. 
 	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
-	rings along the $z$ axis\cite{feng_scalable_2014}, meaning that if one traces the 
-	positions of the aromatic rings with a helical curve, then for each full turn 
-	in the helix, one will encounter two aromatic rings.
-
-	\item \textit{R-alkanes}: A low intensity ring located at r = 1.4
+	rings along the $z$ axis\cite{feng_scalable_2014}.
+        %meaning if one traces the 
+	%positions of the aromatic rings with a helical curve, then for each full turn 
+	%in the helix, one will encounter two aromatic rings.
+
+	\item \textit{R-alkanes}: A low intensity ring located at $|\mathbf{q}|$ = 1.4
 	\AA$^{-1}$ marks the third major reflection of interest. The real space
@@
 	\item \textit{R-pores}: The final feature corresponds to the spacing
-	and symmetry of the d\textsubscript{100} plane. This plane is geometrically
-	related the distance between pores. The feature, which we named R-pores, is
-	characterized by dots along the equatorial axis defined by $q_z$ = 0. The
-	spacing between dots is indicative of the hexagonal symmetry of the packed
-	pores. We observe the same information with higher resolution using SAXS
-	(Fig.~\ref{fig:SAXS}).
+	and symmetry of the pore columns. 
+        %d\textsubscript{100} plane. This plane is geometrically
+        %related the distance between pores.
+	The feature, which we named R-pores, is characterized by reflections along the
+	equatorial axis defined by $q_z$ = 0. The spacing between dots is indicative of
+	the hexagonal symmetry of the packed pores. We observe the same information
+	with higher resolution using SAXS (Fig.~\ref{fig:SAXS}).
 
@@
         \centering
+                \begin{subfigure}[t]{0.495\linewidth}
+                \centering
+                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
+                \caption{}\label{fig:WAXS}
+        \end{subfigure}
 	\begin{subfigure}[t]{0.405\linewidth}
@@
         \end{subfigure}
-        \begin{subfigure}[t]{0.495\linewidth}
-                \centering
-                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
-                \caption{}\label{fig:WAXS}
-        \end{subfigure}
-	\caption{(a) (Reproduced from \citenum{feng_thin_2016}) The repeat spacing
-		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
-		packing. The leading peak, q*, represents the distance between the
-		d\textsubscript{100} planes. Using this distance, we know that the distance
-		between pore centers is 4.12 nm. (b) 2D WAXS gives
-		details about repeating features on the order of angstroms. Experimentalists
-		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
-		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
-		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
-		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
-		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
+	\caption{(a) 2D WAXS gives details about repeating features on the
+		order of angstroms. Experimentalists have explained each of the 5 major
+		reflections present as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack
+		3.7 \AA~apart. (R-double) Monomers arrange vertically in a 2\textsubscript{1}
+		helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer
+		tails are tilted with respect to the membrane plane. (R-pores) As derived from
+		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
+		from \citenum{feng_thin_2016}) The repeat spacing in the 1D small angle X-ray
+		scattering pattern is characteristic of hexagonal packing. The leading peak,
+		q*, represents the distance between the d\textsubscript{100} planes. Using this
+		distance, we know that the distance between pore centers is 4.12 nm.} 
 	\label{fig:SWAXS}
@@
 	bonding network formed by the water may play a role in structuring the pore. We
-	used simulated X-ray diffraction (XRD) patterns to see if there is any
+	used simulated X-ray diffraction (XRD) patterns to uncover any 
+        %see if there is any
 	meaningful structural difference between a "dry" and a "wet" system.
@@
 
-  \subsubsection{\textit{Pair distribution functions and correlation length}}\label{section:correlation_length}
-
-  The normalized pair distribution function, $g(\mathbf{r})$, describes
-  the probability of finding a pair of particles separated by $\mathbf{r}$,
-  \begin{equation}
-	g(\mathbf{r})= \frac{1}{\rho N} \Bigg \langle \sum_{i=1}^{N}\sum_{j\neq i}^{N} \delta(\mathbf{r}+\mathbf{r_j}-\mathbf{r_i}) \Bigg \rangle
-	\label{eqn:correlation}
-  \end{equation}
-  where $\rho$ is the average number density of particles and
-  $\delta(\mathbf{r})$ is the Dirac delta function\cite{kuriabova_linear_2010}.
-  We applied equation \ref{eqn:correlation} in three dimensions and then
-  extracted one dimensional distribution functions using slices of the grid
-  along the appropriate axis.
-
-  We measured the one dimensional pair distribution function, $g(z)$, between centers 
-  of masses of aromatic head group rings along the z-axis (perpendicular to
-  the membrane plane). We averaged all 1D slices in the z-direction of the full 3D 
-  correlation function within 2.1~\AA~of $(x, y)=(0, 0)$. We chose 2.1 \AA~as a crude 
-  approximation of the radius of the phenyl ring plane. 
-  %In this way, we include any instances of 
-  %overlapping electron density which would contribute to R-$\pi$. 
-  We calculated the radius as the sum of the longest C-C distance within a phenyl 
-  ring (2.8~\AA) and two times the carbon atom radius (0.7~\AA).
-
-  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
-  average distance between stacked monomers, and an amplitude that decays exponentially
-  (see Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
-  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
-  to a decaying exponential function of the form:
-  \begin{equation}
-  	Ae^{-z/L}
-  	\label{eqn:decaying_exponential}
-  \end{equation}
-  where A is a fitting parameter for amplitude, z is the independent variable of $g(z)$ 
-  and L is the fit correlation length. We calculated the error in the estimated value
-  of L as the square root of the diagonal entry of the covariance matrix of 
-  optimized fit parameters.  %BJC6: reference scipy curve_fit?
-
-  We also used $g(z)$ to calculate the equilibrated vertical stacking distance between
-  monomers, $d_{equil}$. 
-  %BJC5: in case there is an criticism of this method
-  %The simplest way to do so, would be to Fourier transform
-  %$g(z)$ and extract the highest amplitude frequency of the resulting Fourier series. 
-  %However, the size of our system limits the width of the bins in Fourier space. The bins
-  %are too large to extract a precise value of $\mathit{d}_equil$. Instead, 
-  We fit a decaying sinusoidal function to $g(z)$ of the form:
-  \begin{equation}
-  	1 - A\cos\left(\frac{2\pi}{\mathit{d}_{equil}}z + B\right)e^{-z/L}
-  	\label{eqn:decaying_sinusoid}
-  \end{equation}
-  where A and B are fit parameters for the function's amplitude and phase shift respectively.
-  This function could be used in place of Equation~\ref{eqn:decaying_exponential}, however
-  it does not consistently fit the peaks of $g(z)$ from parallel displaced configurations 
-  well enough to extract a reliable value of L.
-  %BJC5: maybe include plots of these fits in supporting info
-
-% BJC5: I don't plan on showing any 2D correlation functions -- maybe to show swelling
-% of solvated systems.
-
-%  In two dimensions, we observed xy and xz pair distribution functions based on
-%  the center of masses of the aromatic head group rings. For the xy pair
-%  distribution functions, we used a rotated frame of reference. For a given center
-%  of mass, we rotated the coordinates so that the vector created from the center
-%  of mass to the pore center was aligned with the positive x-axis.
-
-  %We gave special
-  %consideration to the xy cross-sections since multiple rings exist in the same
-  %plane located at different vertices of a polygon. We used a rotated frame of
-  %reference to avoid ambiguity in the final pair distribution functions. i
-
-  \subsubsection{\textit{Radial distribution functions}}
-
-  We explored the pores' compositions by measuring the average number densities
-  of various monomer components as a function of distance from the pore centers.
-  We looked at the average number density of sodium ions, aromatic rings and 
-  carbon atoms making up the monomer tails. We binned the radial distance of all
-  atoms in each group from the pore centers, then normalized by the volume of the
-  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}).
-
-  \subsubsection{\textit{Simulated structure factor calculations}}\label{method:xrd}
-
-  We generated simulated XRD patterns based on atomic coordinates in order to make
-  a direct experimental comparison. We modeled all atomic coordinates as Gaussian
-  spheres of electron density corresponding to each atom's electronic radius. A 
-  three dimensional Fourier transform (FT) of the array of electron density results in a three dimensional
-  structure factor which represents the unit cell in reciprocal space. The
-  experimental WAXS measurement was made using a vertically aligned film whose 
-  pores were oriented perpendicular to the direction of the incident X-ray beam. 
+  \subsubsection{\textit{Generation of simulated X-ray diffraction patterns}}\label{method:xrd}
+
+  We generated simulated XRD patterns based on atomic coordinates in order to
+  make a direct experimental comparison. We modeled all atomic coordinates as
+  Gaussian spheres of electron density whose maximum and width are defined by
+  each atom's atomic number electronic radius respectively. A three dimensional
+  Fourier transform (FT) of the array of electron density results in a three
+  dimensional structure factor which represents the unit cell in reciprocal
+  space. The experimental WAXS measurement was made using a vertically aligned
+  film whose pores were oriented perpendicular to the direction of the incident
+  X-ray beam. 
   %BJC6: Below is the part I'm having a hard time putting into words. 
-  Although the pores were vertically aligned, the crystalline domains were still
-  misaligned with respect to the xy plane. To account for this, we averaged
+  Although the pores are vertically aligned, the crystalline domains are
+  still misaligned with respect to the $xy$ plane. To account for this, we averaged
   2D slices of the structure factor at all angles about $|\mathbf{q}| = (0, 0, z)$.
@@
 
-  We measured the intensity of R-pores based on the intensity of the leading peak
-  (closest to $q_r$ = 0) of the $q_r$ cross-section of the patterns at $q_z$=0
-  (Figure~\ref{fig:saxs_xsection}). The beamstop covers most of the small angle
-  reflections in the experimental 2D WAXS pattern. In order to compare the simulated
-  intensity of R-pores to experiment, we used the $q_r$ cross-section of 2D SAXS 
-  which was generated from the same sample. Since the d\textsubscript{110} peak is  %BJC12: verify which crystal plane it is.
-  partially exposed in the experimental 2D WAXS pattern, we normalized the experimental 
-  2D SAXS cross-section by matching the intensity of the d\textsubscript{110} peak 
-  between it and the experimental 2D WAXS cross-section. It is possible that the peak
-  is not fully captured in the 2D WAXS pattern and that our estimate of the intensity
-  of R-pores for the experimental pattern is underestimated.
+  We measured the intensity of R-pores based on the intensity of the
+  d\textsubscript{100} peak (the leading peak closest to $q_r$ = 0) of the $q_r$
+  cross-section of the patterns at $q_z$=0 (Figure~\ref{fig:saxs_xsection}). The
+  beamstop covers most of the small angle reflections in the experimental 2D WAXS
+  pattern. In order to compare the simulated intensity of R-pores to experiment,
+  we used the $q_r$ cross-section of 2D SAXS which was generated from the same
+  sample (Figure S-TBD). Since the d\textsubscript{110} peak is
+  %BJC12: verify which crystal plane it is.  
+  partially exposed in the experimental 2D WAXS pattern, we normalized the
+  experimental 2D SAXS cross-section by matching the intensity of the
+  d\textsubscript{110} peak between it and the experimental 2D WAXS
+  cross-section. It is possible that the peak is not fully captured in the 2D
+  WAXS pattern and that we have underestimated the intensity of R-pores in the
+  experimental pattern.
 
@@
   \caption{(a) We measured the intensity of R-alkanes by calculating the average 
-  intensity within the region bounded by $|\mathbf{q}|$ = 1.4$\AA^{-1}$ and 
-  1.57$\AA^{-1}$ (between 4.0 and 4.5 \AA in real space). We excluded intensities
+  intensity within the region bounded by $|\mathbf{q}|$ = 1.4~$\AA^{-1}$ and 
+  1.57~$\AA^{-1}$ (between 4.0 and 4.5 \AA~in real space). We excluded intensities
   within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
@@
   the R-alkanes region. We took the intensity of R-spots as the average of the 
-  peak intensities near 37 and 143 $\degree$. (d) We measured the intensity of 
-  R-pores by measuring the height of the leading peak (closest to $q_r$=0) of 
-  the cross-section of the diffraction patterns along the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
+  peak intensities near 37 and 143$\degree$. (d) We measured the intensity of 
+  R-pores by measuring the height of the d\textsubscript{100} peak (the leading
+  peak closest to $q_r$=0) of the cross-section of the diffraction patterns along
+  the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
   \end{figure}
 
-  \subsubsection{\textit{Ionic conductivity calculations}}
-
-  We calculated ionic conductivity using the Nernst-Einstein relationship, which 
-  relates the DC ionic conductivity, $\sigma$, to ion diffusivity, $D$, 
-  concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
-  temperature, $T$: 
+  \subsubsection{\textit{Pair distribution functions and correlation length}}\label{section:correlation_length}
+
+  The normalized pair distribution function, $g(\mathbf{r})$, describes
+  the probability of finding a pair of particles separated by $\mathbf{r}$,
   \begin{equation}
-	\sigma = \dfrac{q^2CD}{k_b T} 
-	\label{eqn:nernst_einstein}
+	g(\mathbf{r})= \frac{1}{\rho N} \Bigg \langle \sum_{i=1}^{N}\sum_{j\neq i}^{N} \delta(\mathbf{r}+\mathbf{r_j}-\mathbf{r_i}) \Bigg \rangle
+	\label{eqn:correlation}
   \end{equation}
-  We measured sodium ion diffusion coefficients by calculating the slope
-  of the linear region of the z-direction mean square displacement curve as
-  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
-  visualized the MSD plot to determine where to begin and end a linear fit. We
-  measured ion concentration with respect to the volume of the entire unit cell. 
-  More details are provided in the Supporting Information, Section~S-\ref{S-section:ionic_conductivity}.
+  where $\rho$ is the average number density of particles and
+  $\delta(\mathbf{r})$ is the Dirac delta function\cite{kuriabova_linear_2010}.
+  We applied equation \ref{eqn:correlation} in three dimensions and then
+  extracted one dimensional distribution functions using slices of the grid
+  along the appropriate axis.
+
+  We measured the one dimensional pair distribution function, $g(z)$, between centers 
+  of masses of aromatic head group rings along the z-axis (perpendicular to
+  the membrane plane). We averaged all 1D $z$-directional slices of the full 3D 
+  correlation function within 2.1~\AA~of $(x, y)=(0, 0)$. We chose 2.1 \AA~as a crude 
+  approximation of the radius of the phenyl ring plane. 
+  %In this way, we include any instances of 
+  %overlapping electron density which would contribute to R-$\pi$. 
+  We calculated the radius as the sum of the longest C-C distance within a phenyl 
+  ring (2.8~\AA) and two times the carbon atom radius (0.7~\AA). % citation
+
+  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
+  average distance between stacked monomers, and an amplitude that decays exponentially
+  (see Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
+  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
+  to a decaying exponential function of the form:
+  \begin{equation}
+  	Ae^{-z/L}
+  	\label{eqn:decaying_exponential}
+  \end{equation}
+  where A is a fitting parameter for amplitude, $z$ is the independent variable of $g(z)$ 
+  and L is the fit correlation length. We calculated the error in the estimated value
+  of L as the square root of the diagonal entry of the covariance matrix of 
+  optimized fit parameters.  %BJC6: reference scipy curve_fit?
+
+  We also used $g(z)$ to calculate the equilibrated vertical stacking distance between
+  monomers, $d_{equil}$. 
+  %BJC5: in case there is an criticism of this method
+  %The simplest way to do so, would be to Fourier transform
+  %$g(z)$ and extract the highest amplitude frequency of the resulting Fourier series. 
+  %However, the size of our system limits the width of the bins in Fourier space. The bins
+  %are too large to extract a precise value of $\mathit{d}_equil$. Instead, 
+  We fit a decaying sinusoidal function to $g(z)$ of the form:
+  \begin{equation}
+  	1 - A\cos\left(\frac{2\pi}{\mathit{d}_{equil}}z + B\right)e^{-z/L}
+  	\label{eqn:decaying_sinusoid}
+  \end{equation}
+  where A and B are fit parameters for the function's amplitude and phase shift respectively.
+  This function could be used in place of Equation~\ref{eqn:decaying_exponential}, however
+  it does not consistently fit the peaks of $g(z)$ from parallel displaced configurations 
+  well enough to extract a reliable value of L.
+  %BJC5: maybe include plots of these fits in supporting info
+
+% BJC5: I don't plan on showing any 2D correlation functions -- maybe to show swelling
+% of solvated systems.
+
+%  In two dimensions, we observed xy and xz pair distribution functions based on
+%  the center of masses of the aromatic head group rings. For the xy pair
+%  distribution functions, we used a rotated frame of reference. For a given center
+%  of mass, we rotated the coordinates so that the vector created from the center
+%  of mass to the pore center was aligned with the positive x-axis.
+
+  %We gave special
+  %consideration to the xy cross-sections since multiple rings exist in the same
+  %plane located at different vertices of a polygon. We used a rotated frame of
+  %reference to avoid ambiguity in the final pair distribution functions. i
 
@@
   of its head group. In order to make a system approximately similar to our equilibrated 
-  simulation geometries, we created 4 hexagonally packed pore regions spaced 42.5 \AA 
-  apart, each with 5 columns of scatterers spaced 4.4 \AA apart in the $z$-direction. We
+  simulation geometries, we created 4 hexagonally packed pore regions spaced 42.5 \AA~ 
+  apart, each with 5 columns of scatterers spaced 4.4 \AA~apart in the $z$-direction. We
   built the system 4 times taller in the $z$-direction (80 scatterers per column) in order
@@
   the distance, $d$, between scatterers decays exponentially from $v$ according
-  to the equation $ve^{-d/L}$, where $L$ is the correlation length. We used the
-  experimental correlation length of 9.0 $\AA$.
+  to the equation $ve^{-d/L}$, where $L$ is the correlation length. Unless noted
+  otherwise, we used the experimental correlation length of 9.0 $\AA$.
 
@@
   system are much longer than what we can feasibly simulate.
+
+  \subsubsection{\textit{Radial distribution functions}}
+
+  We explored the pores' compositions by measuring the average number densities
+  of various monomer components as a function of distance from the pore centers.
+  We looked at the average number density of sodium ions, aromatic rings and 
+  carbon atoms making up the monomer tails. We binned the radial distance of all
+  atoms in each group from the pore centers, then normalized by the volume of the
+  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}).
+
+  \subsubsection{\textit{Ionic conductivity calculations}}
+
+  We calculated ionic conductivity using the Nernst-Einstein relationship, which 
+  relates the DC ionic conductivity, $\sigma$, to ion diffusivity, $D$, 
+  concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
+  temperature, $T$: 
+  \begin{equation}
+	\sigma = \dfrac{q^2CD}{k_b T} 
+	\label{eqn:nernst_einstein}
+  \end{equation}
+  We measured sodium ion diffusion coefficients by calculating the slope
+  of the linear region of the $z$-direction mean square displacement curve as
+  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
+  visualized the MSD plot to determine where to begin and end a linear fit. We
+  measured ion concentration with respect to the volume of the entire unit cell. 
+  More details are provided in the Supporting Information, Section~S-\ref{S-section:ionic_conductivity}.
 
@@
   the measured equilibrated pore-to-pore distances. To discern the composition of
-  the monomer layers, addressing question \ref{point:monomernum} above, we ran
+  the monomer layers, addressing Question \ref{point:monomernum} above, we ran
   simulations of systems created with 4--8 columns per pore. We built systems in both
@@
   We can better understand the structure of the system by simulating X-ray
-  diffraction patterns produced from equilibrated MD trajectories and comparing
-  them to experiment (see section~\ref{method:xrd}). We tested systems built with
-  5 columns per pore in the parallel displaced and sandwiched configurations at
+  diffraction patterns produced from equilibrated MD trajectories (see
+  section~\ref{method:xrd}) and comparing them to experiment, addressing
+  Question~\ref{point:xrdmatch}. We tested systems built with 5 columns per pore
+  in the parallel displaced and sandwiched configurations at
   300 K in the ordered and disordered basins, as those were the most consistent
@@
   equilibrated portion of each simulation trajectory (See
-  Section~\ref{method:equil_time}. There are two important factors to take into
+  Section~\ref{method:equil_time}). There are two important factors to take into
   account when looking at differences between experimental XRD and simulated XRD.
@@
   Table~\ref{table:relative_intensities_300K}. Our approach for measuring the intensity of
-  each reflection are described in section S-\ref{S-section:xrd_intensities}. 
+  each reflection is described in Section~\ref{method:xrd}. 
   %MRS12: should that be in Methods instead of suporting?  Not sure.
@@
   	\item The location of R-alkanes (section~\ref{section:ralkanes})
-  	\item The intensity of R-pores (section~\ref{section:rpores})
+  	\item The location and intensity of R-pores (section~\ref{section:rpores})
   \end{itemize}
@@
   R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
-  R-pores    & 12.3       & 49.5       & 54.0      & 50.8       & 53.4               \\
+  R-pores    & 4.91       & 49.5       & 54.0      & 50.8       & 53.4               \\
   R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
@@
   %BJC12: I use the maximum intensity of R-alkanes along the q_r axis at qz=0 to determine its location.
-  The error in the simulated diffraction patterns is less that the error due
+  The error in the simulated diffraction patterns is less than the error due
   binning in each frequency direction, so was not further investigated. 
@@
 
-  R-pores is about 4 times more intense than experiment in all simulated
-  systems. We hypothesize that this is primarily due to the relatively perfect
+  R-pores is about 10 times more intense than experiment in all simulated
+  systems. Some or all of this discrepancy may be a consequence of our
+  normalization of the experimental 2D SAXS pattern, since the common peak
+  between it and the 2D WAXS patterns is partially obscured by the beamstop in
+  the WAXS. If our simulations do indeed predict an intensity of R-pores that is
+  too high, we hypothesize that this is primarily due to the relatively perfect
   infinite hexagonal array of pores in the simulated systems. In the real system,
@@
   average distance between pores. However, there is substantial uncertainty in
-  the exact location relative to the bin size used for the Fourier space
+  the exact location relative to the bin size resulting from the Fourier space
   transformation. We can instead measure the average distance between columns
@@
   showed that we achieve experimentally consistent pore spacings in our
-  simulations in Section~\ref{section:section:mon_per_pore}.
+  simulations in Section~\ref{section:mon_per_pore}.
 
@@
   WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
-  We measured the tilt angle of the alkane chains of the 280K system and found
-  that it equilibrates to an average tilt angle of
-  -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
-  used to explain R-spots. Even when we placed position restraints on the
-  monomers in a tilted initial configuration, monomers quickly reduced their tilt
-  relative to the $xy$ plane to an angle statisically neglibible from zero. (See 
-  Section S-TBD). 
+  We measured the tilt angle of the alkane chains of the 280K system by measuring
+  the angle made by the vector extending from top to bottom of each tail with
+  respect to the membrane plane. We found that it equilibrates to an average tilt
+  angle of -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle
+  previously used to explain R-spots. Even when we placed position restraints on
+  the monomers in a tilted initial configuration, monomers quickly reduced their
+  tilt relative to the $xy$ plane to an angle statisically indistinguishable from
+  zero. (See Section S-TBD). 
   %Similar lack of more than a statistically negligible
@@
   configuration (Figure~\ref{fig:layered_tails}).  This ordering is
-  primarily in the parts of the tail proxmal to the heads, and dies
+  primarily in the parts of the tail proximal to the heads, and dies
   off at the tail ends, where there is more space to fill causing them
-  to pack nearly isotropically. See Section~S-\ref{S-tail_packing} for
+  to pack nearly isotropically. See Section~S-\ref{S-section:tail_packing} for
   a more detailed explanation of the calculation and packing
@@
   of the simulated cross-section (d) is 48\% larger than the experimental 
-  cross-section. Additionally, peak of the simulated $q_z$ cross-section is 
-  located at a somewhat lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
+  cross-section. Additionally, the peak of the simulated $q_z$ cross-section is 
+  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
   \end{figure}
@@
   not surprising since GAFF models atoms as point charges and  % BJC11: need reference %MRS12: just cite the GAFF paper.
-  does not appropriately model the aromatic $\pi-\pi$ interactions, which make
+  does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
   it more energetically favorable for the monomers to stack closer together.  It
@@
   necessarily more tightly packed configuration. However, we equilibrated the
-  system at 500K then annealed it to 300K in an attempt to coerce the tails into
+  system at 500 K then annealed it to 300 K in an attempt to coerce the tails into
   a more tightly packed configuration, however we saw no improvement in packing
-  distance over our 300K models. See section S-TBD for details.
+  distance over our 300 K models. See section S-TBD for details.
 
@@
   same as thermal disorder, but we cannot reach the necssary transition
-  timescales.  
+  timescales for them to show their equivalence.  
   %MRS12: when reworking the first part of the simulation, our hypothesis for the REASONS behind the quenched disorder will ahave to be addressed.
@@
   $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
-  background intensity, as seen in our simulation (blue) by a factor of 3 when we
+  background intensity, relative to systems with simulation levels of disorder (blue)
+  %as seen in simulation (blue) 
+  by a factor of 3 when we
   increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
@@
 
+  %BJC9: Note that the magnitude of the correlation function is much lower than 
+  % in figure 10a. That's because many of the z-slices are zero when you include
+  % all of them.
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.png}
+  \caption{When we average all $z$-slices of the 3D correlation function, the 
+  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
+  \end{figure}
+
   Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
@@
   of the fit implies that the FWHM may be incorrect, and that the radial ordering
-  of the head groups may need improvement.
+  of the head groups may benefit from further optimization.
   %MRS12: is there a structral 
@@
 
-  %BJC9: Note that the magnitude of the correlation function is much lower than 
-  % in figure 10a. That's because many of the z-slices are zero when you include
-  % all of them.
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.png}
-  \caption{When we average all $z$-slices of the 3D correlation function, the 
-  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
-  \end{figure}
-
   We can explain the discrepancies between R-$\pi$ seen experimentally
@@
   of the forcefield to appropriately model $\pi-\pi$ interactions. The intensity
-  of the simulated R-$\pi$ is too high, which may be a consequence of too much
+  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
   ordering in the $z$-direction in addition to high degrees of correlation 
@@
 
-  R-double does not appear in any of the simulated diffraction patterns generated using
-  the systems simulated up to this point. Here we hypothesize a few initial 
-  configurations which may lead to the appearance of R-double and show that we cannot
-  achieve a long-term stable system that exhibits R-double without the inclusion of 
-  small amounts of water in the pores.
+  R-double does not appear in any of the simulated diffraction patterns
+  generated using the systems simulated up to this point. Here we hypothesize a
+  few initial configurations which may lead to the appearance of R-double and
+  show that we cannot achieve a long-term stable system that exhibits R-double
+  without the inclusion of small amounts of water in the pores.
 
@@
 
-  The appearance of R-double implies a vertical modulation in electron density every 7.4 \AA.
-  We are not able to achieve such modulation using our simple initial configurations. Although
-  the position of monomers in parallel displaced configurations alternate every other layer, 
-  such a configuration will not produce R-double, but only off-axis 
-  reflections at the same $q_z$ value~\cite{harburn_atlas_1975}. There is not a unique solution
-  that describes the origin of R-double. Extracting the exact relationship between a diffraction
-  pattern and its real space configuration is well-known as the phase problem~\cite{taylor_phase_2003}.    
-  We have proposed configurations that result in the appearance of R-double below, and we can 
-  speculate which makes the most physical sense. It appears that we cannot achieve a long-term
-  stable system that exhibits R-double without the inclusion of small amounts of water in the pores.
+  The appearance of R-double implies a vertical modulation in electron density
+  every 7.4 \AA. We are not able to achieve such modulation using our simple
+  initial configurations. Although the position of monomers in parallel displaced
+  configurations alternate every other layer, such a configuration will not
+  produce R-double, but only off-axis reflections at the same $q_z$
+  value~\cite{harburn_atlas_1975}. There is not a unique solution that describes
+  the origin of R-double. Extracting the exact relationship between a diffraction
+  pattern and its real space configuration is well-known as the phase
+  problem~\cite{taylor_phase_2003}. We have proposed configurations that
+  result in the appearance of R-double below, and we can speculate which makes
+  the most physical sense. It appears that we cannot achieve a long-term stable
+  system that exhibits R-double without the inclusion of small amounts of water
+  in the pores.
 
@@
 %MRS12: I think it is useful to put in just to show we've been thinking about them.  Can omit the figure in the main text.
- One way to produce R-double if our initial configuration contains alternating parallel and
-anti-parallel carboxylate groups relative to the plane of the monomer's phenyl ring.
-%  (Figure ~\ref{fig:rotated_carboxylate_rzplot_norestraints}). 
-It is difficult to physically justify this system. Systems built this way are
-only stable if position restraints are placed on all head group heavy atoms.
-Carboxylate groups quickly revert to the parallel position as restraints are
-released. There is an appreciable energy barrier that prevents rotation of
-carboxylate groups attached to phenyl rings since the group extends the
-system's $\pi$ conjugation (citation) (See Figure
+  One way to produce R-double is if our initial configuration contains
+  alternating parallel and anti-parallel carboxylate groups relative to the plane
+  of the monomer's phenyl ring.  It is difficult to physically justify this
+  system. Systems built this way are only stable if position restraints are
+  placed on all head group heavy atoms.  Carboxylate groups quickly revert to the
+  parallel position as restraints are released. There is an appreciable energy
+  barrier that prevents rotation of carboxylate groups attached to phenyl rings
+  since the group extends the system's $\pi$ conjugation (citation) (See Figure
   S-\ref{S-fig:carboxylate_dihedral_rb}), which is significant even considering
@@
 
-  One way to could produce R-double if we rotate monomers with respect to vertically adjacent monomers. 
-  In this configuration, monomers are rotated so that the vector created by the  
-  bond extending from the carboxylate carbon to the phenyl ring is oriented $\pm 15 \degree$
-  with respect to the vector extending from the carboxylate carbon to the pore center (Figure
-  ~\ref{fig:rotated_monomers_rzplot_norestraints}). Every other monomer layer is rotated $+15
-  \degree$ and those in between are rotated $-15 \degree$. This configuration allows monomer
-  tails to sit between adjacent monomer tails which may be the most favorable way for them to
-  pack. This configuration is only stable for a few nanoseconds R-double quickly  fades. 
+  Another way to produce R-double is if we rotate monomers with respect to
+  vertically adjacent monomers. In this configuration, monomers are rotated so
+  that the vector created by the bond extending from the carboxylate carbon to
+  the phenyl ring is oriented $\pm 15 \degree$ with respect to the vector
+  extending from the carboxylate carbon to the pore center (Figure
+  ~\ref{fig:rotated_monomers_rzplot_norestraints}). Every other monomer layer is
+  rotated $+15 \degree$ and those in between are rotated $-15 \degree$. This
+  configuration allows monomer tails to sit between adjacent monomer tails which
+  may be the most favorable way for them to pack. This configuration is only
+  stable for a few nanoseconds R-double quickly fades. 
   %MRS12: seems like unnecssary speculation below, since there are a lot of cancelling affects. 
@@
 
-  We can also produce R-double if layers are not uniformly, but instead form
-  pairs that stack less than 3.7~\AA~apart, with center of masses are spaced 7.4
-  \AA~ from neighboring pairs of monomers (Figure
+  We can also produce R-double if monomers are not uniformly spaced in the
+  $z$-direction, but instead form pairs that stack less than 3.7~\AA~apart, with
+  center of masses are spaced 7.4 \AA~ from neighboring pairs of monomers (Figure
   ~\ref{fig:staggered_rzplot_norestraints}). 
@@
 
-  However, the addition of water to the system does promote the appearance of R-double.
+  The addition of water to the system promotes the appearance of R-double, providing
+  an answer to Question~\ref{point:water}.
 %  through the creation of shared hydrogen bonds between water molecules and carboxylate
@@
   Simulated XRD patterns of all other solvated systems tested are shown in Figure
-  S~\ref{S-fig:solvation}, however R-double is not present.
+  S-\ref{S-fig:solvation}, however R-double is not present.
 
@@
   	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers.png}
+  	\label{fig:rotated_monomers}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
   	\includegraphics[width=\textwidth]{staggered.png}
 	\label{fig:staggered}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-  	\centering
-  	\includegraphics[width=\textwidth]{rotated_monomers.png}
-  	\label{fig:rotated_monomers}
   \end{subfigure}
@@
   	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
+  	\label{fig:rotated_monomers_rzplot_restrained}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
   	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.png}
   	\label{fig:staggered_rzplot_restrained}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-  	\centering
-  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
-  	\label{fig:rotated_monomers_rzplot_restrained}
   \end{subfigure}
@@
   	\centering
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
+  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
+  \end{subfigure}
+  \begin{subfigure}{0.3\linewidth}
+  	\centering
   	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png} %BJC5: this needs to be updated
@@
   	\centering
-  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
-  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
-  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
-  	\centering
   	\includegraphics[width=\textwidth]{solvated_offset_rzplot_1.png}
@@
   \end{subfigure}
-  \caption{(a) When monomers are non-uniformly spaced (top), R-double appears if all heavy atoms
-  of the head groups are held in place with position restraints (middle). R-double quickly fades once 
-  the position restraints are released (bottom). (b) When monomer head groups are rotated with respect
-  to vertically adjacent monomers (top), R-double is visible while the heavy atoms of the head groups
-  are held in place with position restraints (middle). Again, R-double fades once the position 
-  restraints are released. (c) When we add 1 wt\% water to the parallel displaced configuration in the
-  ordered basin (top) R-double is not initially present during the restrained portion of equilibration (middle).
-  After 200 ns of equilibration, R-double becomes visible and persists for another 200 ns (bottom).}\label{fig:rdouble}
+  \caption{(a) When monomer head groups are rotated with respect to vertically
+	  adjacent monomers (top), R-double is visible while the heavy atoms of the head
+	  groups are held in place with position restraints (middle). Again, R-double
+	  fades once the position restraints are released. (b) When monomers are
+	  non-uniformly spaced (top), R-double appears if all heavy atoms of the head
+	  groups are held in place with position restraints (middle). R-double quickly
+	  fades once the position restraints are released (bottom). (c) When we add 1
+	  wt\% water to the parallel displaced configuration in the ordered basin (top)
+	  R-double is not initially present during the restrained portion of
+	  equilibration (middle).  After 200 ns of equilibration, R-double becomes
+	  visible and persists for another 200 ns (bottom).}\label{fig:rdouble}
   \end{figure}
@@
 
-  When two vertically stacked monomer head groups hydrogen bond with a shared water 
-  molecule, the monomers are drawn closer together (as illustrated in 
+  When two vertically stacked monomer head groups hydrogen bond with a shared
+  water molecule, the monomers are drawn closer together (as illustrated in
   Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows
-  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
-  with a head group above itself, it will be less likely to share a water molecule 
-  with a head group below it due to geometric constraints. The monomer head group below
-  can just as easily share a water molecule with a head group below itself. In this scenario,
-  the centers of each pair are 2 times the $\pi$-stacking distance apart which would
-  lead to R-double (much like the configuration in Figure~\ref{fig:staggered_rzplot_norestraints}). There are
-  a modest number of occurrences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
-  In order to create Figure~\ref{fig:pore_hbonds}, we binned the $z$-positions of the
-  center of mass of the monomer head groups into 20 bins, the same number as the monomers
-  per columns. This works relatively well since there is a high degree of correlation between
-  columns in our system. Peaks in the distributions represent the scenario where a monomer head group
-  shares a water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
-  we calculated the discrete Fourier transform of the distributions which we used as a rough 
-  indicator of whether the head group arrangement will lead to R-double. We see the 
-  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 
-  0.75 $\AA^{-1}$ are clearly distinguishable, meaning there is periodicity at twice
-  the $\pi$-stacking distance.
+  R-double to appear. If a monomer head group shares a hydrogen bonded water
+  molecule with a head group above itself, it will be less likely to share a
+  water molecule with a head group below it due to geometric constraints. The
+  monomer head group below can just as easily share a water molecule with a head
+  group below itself. In this scenario, the centers of each pair are 2 times the
+  $\pi$-stacking distance apart which would lead to R-double (much like the
+  configuration in Figure~\ref{fig:staggered_rzplot_norestraints}). There are a
+  modest number of occurrences of this scenario, which we quantify in further
+  detail in the Supporting Information, Section S-TBD.
+
+%BJC12: move to supplemental
+%  shown in Figure~\ref{fig:pore_hbonds}. 
+%  In order to create Figure~\ref{fig:pore_hbonds}, we binned the $z$-positions of the
+%  center of mass of the monomer head groups into 20 bins, the same number as the monomers
+%  per columns. This works relatively well since there is a high degree of correlation between
+%  columns in our system. Peaks in the distributions represent the scenario where a monomer head group
+%  shares a water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
+%  we calculated the discrete Fourier transform of the distributions which we used as a rough 
+%  indicator of whether the head group arrangement will lead to R-double. We see the 
+%  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 
+%  0.75 $\AA^{-1}$ are clearly distinguishable, meaning there is periodicity at twice
+%  the $\pi$-stacking distance.
 
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{pore_hbonds.png}
-  \caption{}\label{fig:pore_hbonds}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
-  \caption{}\label{fig:pore_hbonds_ft}
-  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{pore_hbonds.png}
+%  \caption{}\label{fig:pore_hbonds}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
+%  \caption{}\label{fig:pore_hbonds_ft}
+%  \end{subfigure}
   \caption{(a) The structure of the head groups is responsible for the appearance of
@@
 I think %it's likely to be too confusing for many readers as a figure, and takes up too much space.
-(c) We group the $z$-coordinate of the center of mass of monomer
-  head groups into 20 bins. Peaks in the distributions indicate a shared hydrogen bonded
-  water molecule between a monomer head group and one in the bin vertically above it. 
-  The distance between the peaks roughly corresponds to the distance between pairs of 
-  monomers. The distance between peaks in pore 1 (indicated by arrows) is equal to two 
-  times the $\pi$-stacking distance. In this scenario, monomers are no longer evenly spaced
-  in the $z$-direction since they are pulled closer together by hydrogen bonds. (d) We 
-  performed discrete Fourier transforms on each distribution in (c) In Pore 1, there 
-  also periodicity every 8.3 $\AA$, twice the $\pi$-stacking distance, as indicated by the
-  intensity at 0.76 $\AA^{-1}$. In this case, the center of mass of two adjacent pairs 
-  is separated by twice the average monomer stacking distance, while the four monomers 
-  involved are unequally spaced. These conditions seem likely to give rise to R-double.}\label{fig:hbonds}
+%(c) We group the $z$-coordinate of the center of mass of monomer
+%  head groups into 20 bins. Peaks in the distributions indicate a shared hydrogen bonded
+%  water molecule between a monomer head group and one in the bin vertically above it. 
+%  The distance between the peaks roughly corresponds to the distance between pairs of 
+%  monomers. The distance between peaks in pore 1 (indicated by arrows) is equal to two 
+%  times the $\pi$-stacking distance. In this scenario, monomers are no longer evenly spaced
+%  in the $z$-direction since they are pulled closer together by hydrogen bonds. (d) We 
+%  performed discrete Fourier transforms on each distribution in (c) In Pore 1, there 
+%  also periodicity every 8.3 $\AA$, twice the $\pi$-stacking distance, as indicated by the
+%  intensity at 0.76 $\AA^{-1}$. In this case, the center of mass of two adjacent pairs 
+%  is separated by twice the average monomer stacking distance, while the four monomers 
+%  involved are unequally spaced. These conditions seem likely to give rise to R-double.
+  }\label{fig:hbonds}
   \end{figure}
@@
 
-  We are most interested in the structure and composition of the pores since we would like to study
-  transport mechanisms within them. We have shown that the tails possess a certain degree of order
-  which is necessary in order to create the complex WAXS pattern shown experimentally, but
-  they will not be involved in a separation process. We aim to further understand the pore
-  architecture and observe the differences, if any, between the different equilibrated
-  configurations studied so far.
+  We are most interested in the structure and composition of the pores since we
+  would like to study transport mechanisms within them. We have shown that the
+  tails possess a certain degree of order which is necessary in order to create
+  the complex WAXS pattern shown experimentally, but they will not be involved in
+  a separation process. We aim to further understand the pore architecture, in
+  order to address Question~\ref{point:composition}, and observe the differences,
+  if any, between the different equilibrated configurations studied so far.
 
@@
   not cross the x-axis until $\sim$105 ns meaning that tails fully rotate on average about 
-  times over the course of the 400 ns that we studied. Additionally, the correlation 
+  4 times over the course of the 400 ns that we studied. Additionally, the correlation 
   function plateau's near a value of -0.2 which indicates that the tails are starting in 
@@
   3.7 \AA~ apart, the z-dimension of our unit cell should be 7.4 nm. In the ordered basin, 
-  sandwiched system studied in this paper, the z-dimension of the unit cell equilibrated 
+  sandwiched system studied in this paper, the $z$-dimension of the unit cell equilibrated 
   to 8.87 nm, which is roughly consistent with the stacking distance reported in 
   Table~\ref{table:correlation_length}. After 200 ns of annealing from 500K to 300K, the 
-  z-dimension of the unit cell was 9.22 nm. We repeated the annealing procedure over the 
+  $z$-dimension of the unit cell was 9.22 nm. We repeated the annealing procedure over the 
   course of 400 ns and the final z-dimension of the unit cell was 9.20 nm. Much longer
@@
   we simulated infinitely long, aligned pores. The ionic conductivity measurement 
-  to which we are comparing was done with a \SI{80}{\micro\metre} thick film, 
+  to which we are comparing was done with an \SI{80}{\micro\metre} thick film, 
   nearly 10,000 times thicker than our simulated
@@
 
-  We achieve maximum structural consistency with experiment, as determined by simulated
-  2D XRD patterns, when we build our model in the ordered basin parallel displaced
-  configuration with 5 monomer columns per pore and 1 wt\% water. R-alkanes and R-pores
-  appear where expected for the reasons originally predicted. We find that R-spots
-  is likely due to ordered alkane chain packing. R-$\pi$ appears at lower q values than
-  experiment because monomer stack too far apart. Finally, we observed that our model
-  can only produce R-double when we add 1 wt\% water to the system. This observation has
-  possible implications for the reproducibility of the experimental results from Feng 
-  et al. since they claim that their membrane is completely dry.
+  We achieve maximum structural consistency with experiment, as determined by
+  simulated 2D XRD patterns, when we build our model in the ordered basin
+  parallel displaced configuration with 5 monomer columns per pore and 1 wt\%
+  water. R-alkanes and R-pores appear where expected for the reasons originally
+  predicted. We find that R-spots is likely due to ordered alkane chain packing.
+  R-$\pi$ appears at lower q values than experiment because monomer stack too far
+  apart, and its intensity is far too high, likely because our initial
+  configurations contain a high level of dependence between monomer columns.
+  Finally, we observed that our model can only produce R-double when we add 1
+  wt\% water to the system. This observation has possible implications for the
+  reproducibility of the experimental results from Feng et al. since they claim
+  that their membrane is completely dry.
 
@@
   With the structural understanding gained by these simulations, it becomes
-  possible evaluate transport of various solutes within the system, and apply the
+  possible to evaluate transport of various solutes within the system, and apply the
   knowledge gained from this study in order to suggest improvements to the

### 2018-08-21 Ben_Manuscripts/structure_paper/Draft.tex
pass over entire paper.

@@
 %MRS5: could be punchier. I will keep thinking.  I should be the last author.  Chen the names that Joe and Matt wanttu use (presumably with some middle initial?
-\title{Understanding the nanoscale structure of hexagonal phase lyotropic 
-liquid crystal membranes}
+\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
 \author{Benjamin J. Coscia}
@@
 \begin{document}
-
+%MRS13: we might end up adjusting the author list a bit; I will ask Matt where he thinks he and Joe should go.
+I will talk to Rich when we get this going; not clear that he actually has contributed.
+But that's my job.
   \graphicspath{{./figures/}}
@@
 
+  %MRS13: I tweaked this a bit.  Probably could add another sentence to add some of the other important findings.
   Nanostructured porous membranes made from the cross-linked hexagonal phase of
@@
   selective separations. In this work, we investigate an experimentally
-  characterized LLC membrane using an atomistic molecular model. We use
-  simulated X-ray diffraction (XRD) patterns in order to ensure maximum
-  consistency between our structures and experiment. We show that pores are
+  characterized LLC membrane using atomistic molecular modeling. In particular, we compare
+  simulated X-ray diffraction (XRD) patterns with experimental XRD to quantify and understand 
+  differences between simulation and experiment.
+  We find that pores are
   likely composed of 5 columns of stacked LLC monomers which surround each
-  hydrophilic core. Although this system has been reported as dry, we show that
+  hydrophilic core.  We also find that some of the structure previously attributed to 
+  monomer tail tilt is likely instead due to ordered tail packing.  
+  Although this system has been reported as dry, we show that
   small amounts of water are necessary to fully reproduce the experimental XRD
@@
   abrupt partition between the hydrophilic and hydrophobic regions. A caveat is
-  that the time scales of the dynamics are extremely long for this system,
-  requiring starting from a range of alternative initial configurations and
-  careful examination of the metastable states observed. The clearer picture of
+  that the time scales of the dynamics are extremely long for this system, resulting in 
+  simulated structures that appear too ordered, 
+  %MRS13: I left out starting from alternative structures since we didn't actually do it.
+  %requiring starting from a range of alternative initial configurations and
+  and requiring careful examination of the metastable states observed for any conclusions. The clearer picture of
   the nanoscopic structure of these membranes provided in this study will enable
@@
   Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
-  interconnected pores that prevent optimal through-plane transport. The densely packed, 
+  interconnected pores that prevent optimal through-plane transport. In contrast, the densely packed, 
   non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
   the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
-  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
-  liquid crystalline domains, formed when monomers self-assemble, are
-  isotropically aligned which is detrimental to membrane permeability.
+  However, the hexagonally packed liquid crystalline domains of the H\textsubscript{II} phase generally 
+  form isotropically oriented and therefore mutually unaligned domains which are detrimental to membrane 
+  permeability. This domain scale misalignment has inhibited further development of the this technology, and 
+  research efforts were focused on the Q\textsubscript{I} phase, whose geometry does not require alignment~\cite{dischinger_papers}.
 
@@
 
-  Recently, researchers have learned how to macroscopically align the hexagonal
+  However, recently researchers have learned how to macroscopically align the hexagonal
   domains which has revived research into H\textsubscript{II} phase LLC membranes.
-  Previously, research efforts were focused on the Q\textsubscript{I} phase,
-  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
+  In 2014, Feng et al.~showed that one
   can align Col\textsubscript{h} hexagonal domains, created by the monomer Na-GA3C11,
@@
 	the spacing of R-$\pi$ in real space, we will refer to it as R-double. 
-	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
+	R-double has been previously interpreted as 2\textsubscript{1} helical ordering of aromatic
 	rings along the $z$ axis\cite{feng_scalable_2014}.
@@
 	relative intensity.  Accordingly, we name these reflections R-spots. The
-	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
+	location of all spots is $\sim\,37^{\circ}$ from the $q_z$ axis in their
 	respective quadrants. In many liquid crystal systems one can explain the spots
@@
   (Figure~\ref{fig:build_procedure}).
-
+  %MRS13: Would be nice to say we put the scripts on GitHub.  Additional details about which scripts can be in supporting.
+  These initial structures may result in equilibration into slowly-intercoverting metastable states, an issue we will address later in the paper. 
   % BJC5: This needs to be modified to reflect columnar build procedure
@@
 		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
-		placed them into a monoclinic unit cell.}\label{fig:build_procedure}
+		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{fig:build_procedure}
   \end{figure}
@@
   of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
+  %MRS13: be consistent on capitalization of ``Supporting'' ``Information'' and ``section''. Look at JPCB for guidance.
   Supporting information, section S-\ref{S-section:initial_config_dependence}. The 
@@
   equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
-  the z-direction. We explore a second system with an initial spacing of 5
+  the z-direction. We also extensively explored a second system with an initial spacing of 5
   \AA. We briefly explored a third system with an initial spacing of 10
-  \AA. However this spacing yields non-physical behavior which is detailed in the 
+  \AA. However this largest spacing yields non-physical behavior which is detailed in the 
   Supporting Information, section S-\ref{S-section:initial_dbwl}.
@@
   structure to equilibrate for 5 ns in the NPT ensemble with pressure controlled
-  by the berendsen barostat followed by NPT equilibration simulations run for at
+  by the Berendsen barostat followed by NPT equilibration simulations run for at
   least 400 ns using the Parrinello-Rahman barostat. More equilibration details
-  are available in section S-\ref{S-section:equilibration}.
+  are given in section S-\ref{S-section:equilibration}.
 
@@
   based on when the distance between pores stopped changing.  We determined when
-  the distances stopped changing by applying the statistical test,
-  \texttt{pymbar.timeseries.detectEquilibration}, to the time series
-  \cite{chodera_simple_2016,shirts_statistically_2008}. Typically, the pore-to-pore
+  the distances stopped changing by applying the statistical test of Chodera~\cite{chodera_simple_2016},
+  implemented as \texttt{pymbar.timeseries.detectEquilibration}, to the time series. Typically, the pore-to-pore
   distance equilibrated between 200 and 350 ns. We used data collected after 
@@
 
+  %MRS13: I will talk to Matt about getting the code in GitHub.
   We generated simulated XRD patterns based on atomic coordinates in order to
@@
   uniformly.  We applied the same scaling method to the simulated patterns. We
-  carefully chose a scaling factor of $f=3.1$ in order to visibly display all
+  chose a scaling factor of $f=3.1$ in order to visibly display all
   features in all patterns.
@@
   within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
-  simulated patterns differ from experiment in those regions in all cases. (b) We
+  simulated spectra overlap with R-$\pi$ in that region. in those regions in all cases. (b) We
   measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
@@
   the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
+  %MRS13: it's confusing to have the same label (R-spots) beneath c and d.  Should be different labels if different data.
   \end{figure}
@@
   length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
+  %MRS13: I assume a linear least squares fit?  Be precise so it's reproducible.
   to a decaying exponential function of the form:
@@
   In order to gain a deeper understanding of discrepancies between the experimental and
-  and simulated R-$\pi$ reflection, we used a simplified baseline model where we 
+  and simulated R-$\pi$ reflection, we used a simplified model where we 
   represent each monomer as a single point scatterer located at the center of mass
@@
   to the equation $ve^{-d/L}$, where $L$ is the correlation length. Unless noted
-  otherwise, we used the experimental correlation length of 9.0 $\AA$.
+  otherwise, we used the experimental correlation length of 9.0 \AA.
 
@@
   atomistic simulations. The quenched disorder is greater in  magnitude than thermal 
-  disorder (See Table~\ref{table:quenched_disorder} in section~\ref{section:rpi})
-  and inherently includes thermal disorder due to the way we calculate it.
+  disorder (See Table~\ref{table:quenched_disorder} in section~\ref{section:rpi}).
+  %MRS13: you just said this already, commenting out.
+  %and inherently includes thermal disorder due to the way we calculate it.
   This method assumes that the timescales for large scale rearrangements of the
@@
 
-  In order to maximally match the experimental membrane synthesis process,
+  In order to better match the experimental membrane synthesis process,
   we created a cross-linking algorithm that one can apply to equilibrated structures. 
@@
   temperature indeed better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
-  suggesting that our 'effective' temperature might indeed be too high,
+  suggesting that our `effective' temperature might indeed be too high,
   understabilizing structure.
@@
   XRD diffraction pattern with the remaining atoms, which preserves
-  R-spots(Figure~\ref{fig:tails_rzplot}).  Next, we plotted the center
+  R-spots (Figure~\ref{fig:tails_rzplot}).  Next, we plotted the center
   of masses of the first four tail atoms of all tails (Figure
@@
   deviations of the monomers from their average positions during the 
-  production simulations. We hypothesize that the quenched disorder is the 
+  production simulations. We hypothesize that, experimentally, the quenched disorder is the 
   same as thermal disorder, but we cannot reach the necssary transition
-  timescales for them to show their equivalence.  
+  timescales to fully thermalize in these simulations.  
   %MRS12: when reworking the first part of the simulation, our hypothesis for the REASONS behind the quenched disorder will ahave to be addressed.
@@
   produce that shown in Figure~\ref{fig:rdouble_nophenyls}. R-double does not
-  appear without the influence of the head groups. Water molecules must play a
+  appear without the presence of the head groups. Water molecules must therefore play a
   role in the structuring of the head groups since R-double does not appear in
@@
   experiments, we define the pore radius to be 0.6 nm~\cite{zhou_supported_2005}. 
+  %MRS13: be more clear.  ``We define'' would imply from THIS study, but I think you are just talking about other studies.
   %BJC5 : Add vertical line to plots for 'pore radius'? Might be too busy.
@@
   The system does not confine
-  sodium ions and head groups to just within the pore region. For dry systems,
+  sodium ions and head groups to just within this experimentally-defined pore region. For dry systems,
   19\% of sodium ions exist outside the pore region (except sandwiched, ordered basin,
@@
   where 1.5\% are within the pore region). For the solvated system, the results are similar,
-  however the head group density is shifted slightly radially outward. This is likely due to
+  however the head group density is shifted slightly radially outward, due to
   swelling of the pore by water.
@@
   The space in the pore region is filled with a mixture of sodium ions
-  and head groups. The distributions appear somewhat different near r=0, but that noise 
-  is expected since there is significantly less sampling as r approaches 0. Regardless, 
+  and head groups. The distributions appear somewhat different near r=0, but noise 
+  is higher since there is significantly less sampling as r approaches 0. Regardless, 
   all systems, including the solvated system, have a significant number of head groups 
@@
       They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
-	  regions. The biggest differences are at r=0 where noise is expected to be high due to 
+	  regions. The biggest differences are at r=0 where noise is higher due to 
 	  decreased sampling. The center of the pore is not hollow, but contains sodium ions and 
@@
   \cite{dong_translational_1984} and $10^{-14}~m^2/s$ \cite{dvinskikh_molecular_2002}. 
-  We measured the diffusion constants of monomers in each of the systems we studied 
-  (See Table S-\ref{S-table:msd}) and learned that they are all on the order of 
-  $10^{-14}~m^2/s$. This is not entirely surprising considering how densely the 
-  monomers are packed as implied by diffraction experiments. The entangled tails 
+  %MRS13: are these hydrophulic/hydrophopic LC?  Once with electrostatic driving forces are likely 
+  % to be even slower.  We measured the diffusion constants of
+  monomers in each of the systems we studied (See Table
+  S-\ref{S-table:msd}) and learned that they are all on the order of
+  $10^{-14}~m^2/s$. However, since on this timescale, no monomers move
+  a full `level` above or below, this may be an overestimate.  This slow speed is
+  not entirely surprising considering how densely the monomers are
+  packed as implied by diffraction experiments. The entangled tails
   likely restrict both vertical and lateral movement.
@@
   Consequently, there is not enough movement on the timescales we simulated for the system to 
-  consistently reach a structure equivalent to experiment. In all cases our monomers
+  consistently reach a definative equilibrium structure.
+  %MRS13:removed phrase, since long time scale does not guarantee closer to experiment. 
+  %equivalent to experiment. 
+  In all cases our monomers
   equilibrate to a stacking distance that is too large compared to experiment. 
@@
   course of 400 ns and the final z-dimension of the unit cell was 9.20 nm. Much longer
-  annealing simulations may get the system to the correct density, but we do not have
-  the resources to further explore this approach. 
+  annealing simulations may get the system to the correct density, but such simulations are beyond
+  the scope of the current study.
   % 800K simulations are worse. Over 400 ns, the z box dimension goes to 9.8. I think this
@@
   \end{figure}
-
+  %MRS13: would be good to have labels on the upper bar chart x-axis as well. 
 %  The system's structure and physical characteristics did not change
@@
   configurations contain a high level of dependence between monomer columns.
-  Finally, we observed that our model can only produce R-double when we add 1
-  wt\% water to the system. This observation has possible implications for the
+  Finally, we observed that our model can only produce R-double when we add small amounts of
+  % I removed the specific details, since it implied that 2% wouldn't do it, which we don't know.
+  %1 wt\% 
+water to the system. This observation has possible implications for the
   reproducibility of the experimental results from Feng et al. since they claim
@@
   also observed that there is not a hard partition between hydrophilic and
-  hydrophobic regions, rather there is a gradient. This finding has raised
+  hydrophobic regions; instead, there is a gradient of chemical constituents. This finding raises
   questions about the nature of size-exclusion separations in systems without a
-  well-defined pore size, which potentially could give rise to separations that
+  well-defined pore size, which potentially could enable separations that
   vary with chemical identity as well as size.
@@
   cross-linked by the algorithm we implemented. The diffraction pattern weakens
-  relative to the uncross-linked system, the ionic conductivity drops by a factor
+  relative to the uncross-linked system, 
+  %MRS13: I might have missed you mentioning this point before? Make sure it is in the results text.
+  ionic conductivity drops by a factor
   of ca. 1.5, in closer agreement with experiment, the pore spacing decreases and
@@
 
-  With the structural understanding gained by these simulations, it becomes
+  With the structural understanding gained by these simulations, it will becomes
   possible to evaluate transport of various solutes within the system, and apply the

### 2018-08-27 Ben_Manuscripts/structure_paper/supporting_information.tex
Reorganizing supporting info

@@
 
-  \section{Attempted Self-assembly}\label{section:self_assembly}
-
-  We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
-  generated using Packmol \cite{martinez_packmol:_2009} (Figure~\ref{fig:isotropic_box}).
-  The input file given to Packmol is shown below.
-
-  \lstset{language=bash}
-  \begin{lstlisting}
-  tolerance 2.0
-  output packed.pdb
-  filetype pdb
-  structure monomer.pdb
-  		number 400
-  		inside box 0. 0. 0. 84.3 84.3 84.3
-  end structure
-  \end{lstlisting}
-
-  We used the same number of monomers (400) that we used in all other simulations. 
-  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
-  box with a volume of 660 $nm^3$, 25\% larger than those used to create ordered unit
-  cells we studied. We tested systems with semi-isotropic and anisotropic pressure 
-  coupling since the shape of the unit cell will likely need to change in order to 
-  accommodate hexagonally packed pores.
-
-  We use the nematic order parameter as defined in section~\ref{method:nematic_order} to 
-  observe any progress towards system ordering. In both cases, we see that the nematic
-  order parameter stays close to zero for the duration of the simulation time, indicating
-  an isotropic arrangement of head groups (Figure~\ref{fig:nematic_isotropic}). The values
-  are slightly negative since there are only 400 monomers. 
-  Equation~\ref{eqn:nematic_order_parameter} is bounded between -1 and 1, however, with a
-  proper choice of nematic director, measured values will range between 0 and 1. With a 
-  large number of samples, an isotropic system would have an order parameter of 0.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{isotropic_box.png}
-  \caption{}\label{fig:isotropic_box}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{nematic_isotropic.png}
-  \caption{}\label{fig:nematic_isotropic}
-  \end{subfigure}
-  \caption{(a) We created a box of isotropically packed monomers and allowed it to simulate
-  for 100 ns using isotropic and anisotropic pressure coupling. (b) The nematic order 
-  parameter hovers close to zero for the duration of the simulation meaning the system
-  maintains its isotropic alignment.}\label{fig:self_assembly}
-  \end{figure}
-
   \section{Further details regarding monomer parameterization}\label{section:parameterization}
 
-  \vspace{1em}
   We parameterized monomers according to the following procedure:
@@
   \end{enumerate} 
-
+  \clearpage
   \begin{figure}[!htb]
@@
 
-  \begin{figure}[!htb]
-	\centering
-        \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
-	\caption{The groups used for radial distribution calculations. Red atoms are in the
-		tails group. Green atoms are in the head group region. The blue atom is sodium. 
-		}\label{fig:monomer_color_coded}
-  \end{figure}
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=0.5\textwidth]{monomer_dihedrals.png}
-  \caption{We measured the autocorrelation functions of the dihedrals highlighted in
-  black. We only included dihedrals associated with the outer tails in our calculation
-  since the position of the center tail leads to fundamentally different interactions and
-  dynamics.}\label{fig:dihedrals}
-  \end{figure}
-
-  \begin{figure}[!htb]
-        \centering
-        \begin{subfigure}[b]{0.32\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{sandwiched.png}
-                \caption{}\label{fig:sandwiched}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.32\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{PD.png}
-                \caption{}\label{fig:pd}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.32\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{Tshaped.png}
-                \caption{}\label{fig:tshaped}
-        \end{subfigure}
-        \vskip\baselineskip
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{sandwichedlayers.png}
-                \caption{}\label{fig:sandwichedlayers}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.475\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{offsetlayers.png}
-                \caption{}\label{fig:offsetlayers}
-        \end{subfigure}
-        \caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
-        3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart.
-        (d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
-        configuration }\label{fig:stacking}
-  \end{figure}
-
-  \begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{pore_radius_illustration.png}
-	\caption{When creating an initial configuration, the pore radius is defined based
-	on the distance of the carbonyl carbon from the pore's central axis}
-	\label{fig:pore_radius_illustration}
-  \end{figure}
-
-  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.
-
-  \section{Number of monomers per column}\label{section:monomers_per_column}
-
-  We chose to build all systems using 20 monomers per column. We made this choice
-  by considering a number of factors that directly affect the quality of our results. 
-  Clearly, choosing a small number of layers will cause the system to suffer from 
-  finite size effects. Even in our 20 monomer-per-column system, axial correlations
-  between stacked monomers persist throughout the entire correlation function (see
-  Figure ~\ref{M-fig:correlation}). The correlation function of the system which we
-  built with 40 monomers per column continues to oscillate for its full length
-  (Figure~\ref{fig:tall_correlation_full}). If we continue adding monomers, the 
-  correlation function will eventually fully decay but it is not worth the 
-  computational expense. Regardless, the correlation lengths calculated from 20
-  monomer per column simulations are in sufficient agreement with experiment.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{tall_correlation_full.png}
-  \caption{Oscillations persist throughout the length of the correlation 
-  function for the sandwiched system in the ordered basin built with 40 monomers
-  per column. The full system is ca. 17 nm tall so the full correlation function
-  covers half this length since periodicity forces the remaining length to be its
-  mirror image.}\label{fig:tall_correlation_full}
-  \end{figure}
-
-  We may be able to simulate systems using less than 20 monomers per column, but chose
-  to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
-  patterns. The size of the Fourier space bin in each dimension is determined by 
-  $dfrac{2\pi}{L}$ where L is the length of a given box vector. The z-box vector 
-  for 20 monomer-per-column systems is $\approx$ 85 \AA which means we will see 
-  a reciprocal space resolution of 0.074 \AA$^{-1}$ in the z direction. Further decreasing
-  the resolution would increase the noise in the simulated patterns and make it more
-  difficult to measure the intensity of reflections of interest.
+  \section{Attempted Self-assembly}\label{section:self_assembly}
+
+  We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
+  generated using Packmol \cite{martinez_packmol:_2009} (Figure~\ref{fig:isotropic_box}).
+  The input file given to Packmol is shown below.
+
+  \lstset{language=bash}
+  \begin{lstlisting}
+  tolerance 2.0
+  output packed.pdb
+  filetype pdb
+  structure monomer.pdb
+  		number 400
+  		inside box 0. 0. 0. 84.3 84.3 84.3
+  end structure
+  \end{lstlisting}
+
+  We used the same number of monomers (400) that we used in all other simulations. 
+  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
+  box with a volume of 660 $nm^3$, 25\% larger than those used to create ordered unit
+  cells we studied. We tested systems with semi-isotropic and anisotropic pressure 
+  coupling since the shape of the unit cell will likely need to change in order to 
+  accommodate hexagonally packed pores.
+
+  We use the nematic order parameter as defined in section~\ref{method:nematic_order} to 
+  observe any progress towards system ordering. In both cases, we see that the nematic
+  order parameter stays close to zero for the duration of the simulation time, indicating
+  an isotropic arrangement of head groups (Figure~\ref{fig:nematic_isotropic}). The values
+  are slightly negative since there are only 400 monomers. 
+  Equation~\ref{eqn:nematic_order_parameter} is bounded between -1 and 1, however, with a
+  proper choice of nematic director, measured values will range between 0 and 1. With a 
+  large number of samples, an isotropic system would have an order parameter of 0.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{isotropic_box.png}
+  \caption{}\label{fig:isotropic_box}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{nematic_isotropic.png}
+  \caption{}\label{fig:nematic_isotropic}
+  \end{subfigure}
+  \caption{(a) We created a box of isotropically packed monomers and allowed it to simulate
+  for 100 ns using isotropic and anisotropic pressure coupling. (b) The nematic order 
+  parameter hovers close to zero for the duration of the simulation meaning the system
+  maintains its isotropic alignment.}\label{fig:self_assembly}
+  \end{figure}
 
   \section{Initial Configuration Dependence}\label{section:initial_config_dependence}
-%  \begingroup
-%	\fontsize{14pt}{12pt}\selectfont
-%	\textbf{Initial Configuration Dependence}
-%  \endgroup
-
-  \vspace{1em}
+
   We addressed any major dependence on initial configuration in the main text.
   There we showed that systems are stable when made with 4, 5, 6, 7, and 8
-  monomers per layer. We also showed that systems are stable when monomer head
+  columns per pore. We also showed that systems are stable when monomer head
   groups are oriented in the parallel displaced and sandwiched configurations
   (see Figure~\ref{fig:stacking}). Our model is most consistent with experiment
-  when built with 5 monomers per layer, with layers stacked 3.7 \AA~apart in 
+  when built with 5 columns per pore, with monomers stacked 3.7 \AA~apart in 
   the parallel displaced configuration.
@@
   There are three other parameters whose choice may influence the equilibrium
-  structure: initial pore spacing, initial pore radius and initial distance
-  between layers. Here we show the results of a sensitivity analysis performed
+  structure: initial pore spacing, initial pore radius and initial stacking distance
+  between monomers. Here we show the results of a sensitivity analysis performed
   on the three parameters. To reduce the size of the sensitivity analysis, we
-  only tested systems built with 5 monomers per layer with layers stacked in 
+  only tested systems built with 5 columns per pore with monomers stacked in 
   the parallel displaced configuration. We equilibrated all systems according
@@
 
-  %\begin{enumerate}
-
-  %	  \item \underline{Initial pore spacing}
   \subsection{Initial pore spacing}\label{section:initial_pore_spacing}
@@
   (Figure~\ref{fig:p2p_diagram}). To reduce the number of variables, we held the
-	  pore radius constant, at 6 \AA~and the distance between layers at 3.7 \AA~since
+  pore radius constant, at 5 \AA~and the distance between layers at 3.7 \AA~since
   those were the values used in our optimal system in the main text. We
@@
   between columns which disrupts equilibration. If the pore spacing is too large
-	  the pores squeeze together, but in a distorted hexagonal array because the xy
+  the pores squeeze together, but in a distorted hexagonal array because the $xy$
   initial translation of the pores is somewhat erratic.
@@
 	avoiding a system such as this where vacuum gaps between pore columns are
-		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
-%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
- %               spacing of 3.99 \AA~ which distorts the hexagonal array.
+	introduced unnecessarily. 
+	%The system equilibrates to a pore spacing of 4.27
+    %$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
+    %spacing of 3.99 \AA~ which distorts the hexagonal array.
 
@@
 
-	  \begin{figure}[!htb]
-		\centering
-		\includegraphics[width=0.4\textwidth]{p2p_diagram.png}
-		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
-		equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
-		are the same.}~\label{fig:p2p_diagram}
-	  \end{figure}
-
-	  %BJC: Could put vertical lines to indicate where position restraint values are reduced
+	% BJC: Could put vertical lines to indicate where position restraint values are reduced
   	\begin{figure}[!htb]
@@
 	\end{subfigure}
-
+	\begin{subfigure}{0.3\textwidth}
+	\includegraphics[width=\textwidth]{p2p_diagram.png}
+	\caption{}~\label{fig:p2p_diagram}
+%		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
+%		equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
+%		are the same.}~\label{fig:p2p_diagram}
+  	\end{subfigure} 
 	\caption{The pore spacing during the restrained portion of the
-			dry equilibration procedure is shown. Every 50 ps (0.05 ns) position restraints
-			are reduced according to the sequence: 1000000, 3162, 56, 8, 3, 2, 1, 0 kJ
-			mol$^{-1}$ nm$^{-2}$. When the initial pore spacing is chosen below the
-			experimental value (a) or at the experimental value (b), there is an abrupt
-			change in pore spacing when the position restraints are reduced to 56 kJ
-			mol$^{-1}$ nm$^{-2}$. When pores are started 45 \AA~apart (c) the pore spacing
-			remains relatively stable. When pores are spaced 50 \AA~apart (d), the pore
+	dry equilibration procedure is shown. Every 50 ps (0.05 ns) we reduce the 
+	force constant on the position restraints according to the sequence: 1000000,
+	3162, 56, 8, 3, 2, 1, 0 kJ mol$^{-1}$ nm$^{-2}$. When we chose an initial pore
+	spacing below experimental value (a) or at the experimental value (b), there
+	is an abrupt change in pore spacing when the position restraints are reduced to 56 kJ
+	mol$^{-1}$ nm$^{-2}$. When we initially position pores 45 \AA~apart (c) the pore spacing
+	remains relatively stable. When we initially place pores 50 \AA~apart (d), the pore
 	spacing decreases nearly linearly once the restraints are reduced to 56 kJ
-			mol$^{-1}$ nm$^{-2}$. When pores are spaced 55 \AA~apart (e), so that monomers
+	mol$^{-1}$ nm$^{-2}$. When we initially place pores 55 \AA~apart (e), so that monomers
 	do not intersect with adjacent pores, and position restraints are reduced to 56
 	kJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
-			when force constants are reduced below 3 kJ mol$^{-1}$ nm$^{-2}$.} 
+	when force constants are reduced below 3 kJ mol$^{-1}$ nm$^{-2}$. (f)
+	In a perfect hexagonal, there are 5 distances that should be exactly
+	equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
+	are the same. All plots in (a)--(e) are the average of these distances.} 
 	\label{fig:p2p}
@@
 
-%	  \item \underline{Initial pore radius}
   \subsection{Initial pore radius}\label{section:initial_pore_radius}
@@
   Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
-	  pore spacing constant at 45 \AA~and the initial distance between layers
+  pore spacing constant at 45 \AA~and the initial stacking distance between monomers
   constant at 3.7 \AA. Equilibrated values of pore radii are presented in
@@
   Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
-	  Statistics for the pore radii reported were generated from the time series
+  We generated statistics for the pore radii reported from the time series
   representing the average pore radius at each frame. We detected equilibration
-	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
-	  and standard deviation of pore radii using only data points collected after
-	  equilibration was detected.
+  as described in Section~\ref{M-method:equil_time} of the main text. We 
+  calculated the average and standard deviation of pore radii using only data 
+  points collected after equilibration was detected.
 
@@
   system does not have a concrete meaning since slits do not have a single
-		radius, but its calculated value is reported in Table ~\ref{table:radii}. We
+  radius, but its calculated value is still reported in Table ~\ref{table:radii}. We
   are wary of such a non-symmetric structure and choose not to use a pore radius
@@
   \centering
+  \begin{minipage}{0.475\textwidth}
+  \centering
+  \includegraphics[width=0.8\textwidth]{pore_radius_illustration.png}
+  \caption{When creating an initial configuration, we define the pore radius,
+  $\mathbf{R}$, based on the distance of the carbonyl carbon from the pore's
+  central axis.}~\label{fig:pore_radius_illustration}
+  \end{minipage}\qquad
+  \begin{minipage}{0.475\textwidth}
+  \centering
+  \vspace{4em}
   \includegraphics[width=\textwidth]{slit_pores.png}
-	  \caption{A system that was built with an initial pore radius of 8
-		  \AA~equilibrates to a structure that exhibits both cylindrical and slit-like
-		  pores. As pictured here, sodium ions are colored blue, carbon atoms in the
-		  aromatic ring of the head group are colored orange and all else is colored
-		  cyan.}~\label{fig:slits}
-	  \end{figure}
-
-%	  \item \underline{Initial distance between layers}
-	  \subsection{Initial distance between layers}\label{section:initial_dbwl}
-
-	  We tested 3 different initial layer spacings, defined as the distance
-	  between the planes of aromatic rings in each layer. Systems built with layers
+  \vspace{1em}
+  \caption{A system that was built with an initial pore radius of 8~\AA~equilibrates
+  to a structure that exhibits both cylindrical and slit-like pores. As pictured 
+  here, sodium ions are colored blue, carbon atoms in the aromatic ring of the head 
+  group are colored orange and all else is colored cyan.}~\label{fig:slits}
+  \end{minipage}
+  \end{figure}
+
+  \subsection{Initial stacking distance between monomers}\label{section:initial_dbwl}
+
+  We tested 3 different initial monomer spacings, defined as the $z$-distance
+  between the planes of aromatic rings. Systems built with layers
   stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
@@
 	\centering
-		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
+	\includegraphics[width=0.3\textwidth]{dbwl_10.png}
 	\caption{When layers are initially stacked 10 \AA~apart and the system
@@
 
-%  \end{enumerate}
-
-%  \noindent
-%  \begingroup
-%        \fontsize{14pt}{14pt}\selectfont
-%	\textbf{Calculation of pore-to-pore spacing statistics}
-%  \endgroup
-
-  \begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
-	\caption{There are five pore-to-pore distances that are equal in a perfect
-		hexagon. If each number in the diagram represents the center of a
-		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
-		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
-		are independent. For example, the distance from 1 to 4 is defined by
-		the location of all other pore centers.}
-	\label{fig:p2p_diagram}
-  \end{figure}
+  \clearpage
+  \section{Placement of monomer head groups}
+
+  The monomer head groups consist of a substituted benzene ring which may participate in
+  $\pi-\pi$ stacking interactions. There are three $\pi-\pi$ stacking modes known
+  to occur in nature: sandwiched, parallel displaced and T-shaped
+  (Figures~\ref{fig:sandwiched}--\ref{fig:tshaped})~\cite{sinnokrot_estimates_2002}.
+  We ruled out the T-shaped configuration because its vertical stacking distance is
+  inconsistent with experimental spectroscopy. Additionally, steric interactions
+  between the bulky alkane tails make this motif unfavorable. We chose to explore
+  systems in both the sandwiched and parallel displaced configurations since their
+  stacking distances are both consistent with experimental diffraction patterns.
+
+  \begin{figure}[!htb]
+        \centering
+        \begin{subfigure}[b]{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{sandwiched.png}
+                \caption{}\label{fig:sandwiched}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{PD.png}
+                \caption{}\label{fig:pd}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.32\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{Tshaped.png}
+                \caption{}\label{fig:tshaped}
+        \end{subfigure}
+        \vskip\baselineskip
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{sandwichedlayers.png}
+                \caption{}\label{fig:sandwichedlayers}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.475\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{offsetlayers.png}
+                \caption{}\label{fig:offsetlayers}
+        \end{subfigure}
+        \caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
+        3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart.
+        (d) Monomers stacked in the sandwiched configuration (e) Monomers stacked in the parallel-displaced
+        configuration.}\label{fig:stacking}
+  \end{figure}
+
+  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.
+
+  \section{Number of monomers per column}\label{section:monomers_per_column}
+
+  We chose to build all systems using 20 monomers per column. We made this choice
+  by considering a number of factors that directly affect the quality of our results. 
+  Clearly, choosing a small number of layers will cause the system to suffer from 
+  finite size effects. Even in our 20 monomer-per-column system, axial correlations
+  between stacked monomers persist throughout the entire correlation function (see
+  Figure ~\ref{M-fig:correlation}). The correlation function of the system which we
+  built with 40 monomers per column is very similar to that created with 20 monomers
+  per columns (continues to oscillate for its full length
+  (Figure~\ref{fig:tall_correlation_full}). If we continue adding monomers, the 
+  correlation function will eventually fully decay but it is not worth the 
+  computational expense. Regardless, the correlation lengths calculated from 20
+  monomer per column simulations are in sufficient agreement with experiment.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{z_correlation_overlay.png}
+  \caption{}\label{fig:z_correlation_overlay}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{tall_correlation_full.png}
+  \caption{}\label{fig:tall_correlation_full}
+  \end{subfigure}
+  \caption{(a) The correlation functions generated from ordered basin sandwiched 
+  configurations are nearly the same when the $z$-dimension of the system is doubled.
+  (b) Oscillations persist throughout the length of the correlation function for the
+  sandwiched system in the ordered basin built with 40 monomers per column. The full
+  system is ca. 17 nm tall so the full correlation function covers half this length
+  since periodicity forces the remaining length to be its mirror image.}\label{fig:correlation_functions}
+  \end{figure}
+
+  We may be able to simulate systems using less than 20 monomers per column, but chose
+  to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
+  patterns. The size of the Fourier space bin in each dimension is determined by 
+  $\dfrac{2\pi}{L}$ where L is the length of a given box vector. The $z$-box vector 
+  for 20 monomer-per-column systems is $\approx$ 85 \AA which means we will see 
+  a reciprocal space resolution of 0.074 \AA$^{-1}$ in the z direction. Further decreasing
+  the resolution would increase the noise in the simulated patterns and make it more
+  difficult to measure the intensity of reflections of interest.
 
@@
 
-  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
-
- %BJC: is it really necessary to explain this if I release the code? I don't explain
- %any of the other stats I calculate.
-  \vspace{1em} 
-  We are interested in 5 pore-to-pore distances which should all be
-  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
-  the 5 distances are independent. We can calculate a trajectory of spacing
-  versus time for each of the 5 distances. We calculated the average pore-to-pore
-  spacing and its uncertainty according to the following procedure:
-   \begin{enumerate}
-	\item We calculated the time when each of the pore-to-pore distances
-	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
-	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
-	after the largest of the five values.
-	\item We calculated how long it takes for the data in each of the 5
-	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
-	\cite{chodera_simple_2016,shirts_statistically_2008}. 
-	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
-	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
-	five sub-trajectories of pore-to-pore spacings.   
-	\item We generate statistics using the bootstrapping technique. For
-	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
-	sampling from the trajectory blocks. 
-	\item The average pore-to-pore distance is the mean of all pore
-	spacings among all bootstrap trials.
-	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
-	pore spacing for each pore over all bootstrap trials. Using the 5 average 
-	pore-to-pore distances, we calculate the spread with:
-	\begin{equation}
-	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
-	\label{equation:p2p_stats}
-	\end{equation}
-	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
-	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
-	spacings.
-
-  \end{enumerate}
+%  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
+% 
+% %BJC: is it really necessary to explain this if I release the code? I don't explain
+% %any of the other stats I calculate. 
+%  We are interested in 5 pore-to-pore distances which should all be
+%  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
+%  the 5 distances are independent. We can calculate a trajectory of spacing
+%  versus time for each of the 5 distances. We calculated the average pore-to-pore
+%  spacing and its uncertainty according to the following procedure:
+%   \begin{enumerate}
+%	\item We calculated the time when each of the pore-to-pore distances
+%	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
+%	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
+%	after the largest of the five values.
+%	\item We calculated how long it takes for the data in each of the 5
+%	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
+%	\cite{chodera_simple_2016,shirts_statistically_2008}. 
+%	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
+%	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
+%	five sub-trajectories of pore-to-pore spacings.   
+%	\item We generate statistics using the bootstrapping technique. For
+%	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
+%	sampling from the trajectory blocks. 
+%	\item The average pore-to-pore distance is the mean of all pore
+%	spacings among all bootstrap trials.
+%	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
+%	pore spacing for each pore over all bootstrap trials. Using the 5 average 
+%	pore-to-pore distances, we calculate the spread with:
+%	\begin{equation}
+%	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
+%	\label{equation:p2p_stats}
+%	\end{equation}
+%	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
+%	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
+%	spacings.
+%	
+%  \end{enumerate}
+%  \begin{figure}[!htb]
+%	\centering
+%	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
+%	\caption{There are five pore-to-pore distances that are equal in a perfect
+%		hexagon. If each number in the diagram represents the center of a
+%		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
+%		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
+%		are independent. For example, the distance from 1 to 4 is defined by
+%		the location of all other pore centers.}
+%	\label{fig:p2p_diagram}
+%  \end{figure}
 
@@
 
-  \begin{figure}[!htb]
-
+  \clearpage
+
+  \begin{figure}[!htb]
   \begin{subfigure}{\linewidth}
@@
         \end{subfigure}
-
   \end{subfigure}
@@
 
-  \section{Measurement of intensities of experimental and simulated XRD patterns}\label{section:xrd_intensities}
-
-  We developed standardized methods of measuring the intensity of reflections of interest
-  in the experimental and simulated X-ray diffraction patterns presented in this work. Here,
-  we graphically illustrate the methods used for measuring these intensities.
-
-  All diffraction patterns are normalized according to R-alkanes and the intensities
-  of all reflections are reported relative to the intensity of R-alkanes. The region
-  used to calculate the average intensity of R-alkanes is shown in 
-  Figure~\ref{fig:ralkanes}. The top region is excluded because, in the simulated
-  patterns, R-$\pi$ intersects with R-alkanes.
-
-  R-$\pi$ and R-double are reported as the maximum values of the peaks of the 
-  $q_z$ cross-section of the experimental pattern at $q_r=0$ (Figure~\ref{fig:rpi_rdouble}).
-  In the case of the experimental pattern, the peak heights are not symmetrical,
-  so we report the average of the two heights.
-
-  We measured R-spots by calculating the average intensity within a region 
-  selected by visual inspection. We report the average intensity within the regions 
-  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernible
-  spots, we report the average intensity at the intersection of R-alkanes with
-  the $q_z$ value of R-double since that is where we expect it to appear based on
-  experiment. Since R-double does not appear in our simulated patterns, we 
-  estimate where it should appear as half of the $q_z$ value of R-$\pi$.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\linewidth}
-  \centering
-  \includegraphics[width=\textwidth]{WAXS_raw.png}
-  \caption{Unaltered experimental WAXS pattern}\label{fig:unaltered}
-  \end{subfigure}
-  \begin{subfigure}{0.45\linewidth}
-  \centering
-  \includegraphics[width=\textwidth]{ralkanes.png}
-  \caption{R-alkanes}\label{fig:ralkanes}
-  \end{subfigure}
-  \begin{subfigure}{0.45\linewidth}
-  \centering
-  \includegraphics[width=\textwidth]{rpi_rdouble.png}
-  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
-  \end{subfigure}
-  \begin{subfigure}{0.45\linewidth}
-  \centering
-  \includegraphics[width=\textwidth]{rspots.png}
-  \caption{R-spots}\label{fig:rspots}
-  \end{subfigure}
-  \caption{}\label{fig:xrd_intensities}
-  \end{figure}
+%BJC: now in main text
+%  \section{Measurement of intensities of experimental and simulated XRD patterns}\label{section:xrd_intensities}
+%  
+%  We developed standardized methods of measuring the intensity of reflections of interest
+%  in the experimental and simulated X-ray diffraction patterns presented in this work. Here,
+%  we graphically illustrate the methods used for measuring these intensities. 
+%  
+%  All diffraction patterns are normalized according to R-alkanes and the intensities
+%  of all reflections are reported relative to the intensity of R-alkanes. The region
+%  used to calculate the average intensity of R-alkanes is shown in 
+%  Figure~\ref{fig:ralkanes}. The top region is excluded because, in the simulated
+%  patterns, R-$\pi$ intersects with R-alkanes.
+%  
+%  R-$\pi$ and R-double are reported as the maximum values of the peaks of the 
+%  $q_z$ cross-section of the experimental pattern at $q_r=0$ (Figure~\ref{fig:rpi_rdouble}).
+%  In the case of the experimental pattern, the peak heights are not symmetrical,
+%  so we report the average of the two heights.
+%  
+%  We measured R-spots by calculating the average intensity within a region 
+%  selected by visual inspection. We report the average intensity within the regions 
+%  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernible
+%  spots, we report the average intensity at the intersection of R-alkanes with
+%  the $q_z$ value of R-double since that is where we expect it to appear based on
+%  experiment. Since R-double does not appear in our simulated patterns, we 
+%  estimate where it should appear as half of the $q_z$ value of R-$\pi$.
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\linewidth}
+%  \centering
+%  \includegraphics[width=\textwidth]{WAXS_raw.png}
+%  \caption{Unaltered experimental WAXS pattern}\label{fig:unaltered}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\linewidth}
+%  \centering
+%  \includegraphics[width=\textwidth]{ralkanes.png}
+%  \caption{R-alkanes}\label{fig:ralkanes}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\linewidth}
+%  \centering
+%  \includegraphics[width=\textwidth]{rpi_rdouble.png}
+%  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\linewidth}
+%  \centering
+%  \includegraphics[width=\textwidth]{rspots.png}
+%  \caption{R-spots}\label{fig:rspots}
+%  \end{subfigure}
+%  \caption{}\label{fig:xrd_intensities}
+%  \end{figure}
 
@@
 
-  The magnitude of noise in the simulated diffraction patterns decrease as 
-  the number of independent configurations increases. We simulated the structure
-  factor of 100 randomly placed particles and varied the number of independent 
-  configurations (N). It is expected that the structure factor should resemble
-  a two-dimensional Gaussian. We cannot sample enough independent configurations
-  of our system to completely eliminate noise.
+  The magnitude of noise in the simulated diffraction patterns decreases as 
+  the number of independent configurations increases (Figure~\ref{fig:xrd_noise}).
+  We simulated the structure factor of 100 randomly placed particles and varied 
+  the number of independent configurations (N). It is expected that the structure
+  factor should resemble a two-dimensional Gaussian. We cannot sample enough 
+  independent configurations of our system to completely eliminate noise.
 
@@
 
-  \section{Experimental correlation length of R-$\pi$}\label{section:correlation_length}
-
-  \vspace{1em}
-  Previous experimental studies of these systems did not calculate the correlation length, so we estimated it
-  from the raw 2D WAXS data. We took a slice of the 2D WAXS data along the dashed line in
-  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
-  intensity far from the pattern (high $q$) uniformly. We used a least squares
-  algorithm to fit a Lorentzian curve to the data. Only values recorded above
-  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
-  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
-  maximum (FWHM) is related to the correlation length, L, by the relationship: $
-  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
-  of the diagonal entry of the covariance matrix of optimized fit parameters.
-  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
-  method. Since the experimental peak width is also influenced by strain and 
-  instrumental broadening in addition to finite size broadening, the value 
-  calculated here is really only an upper bound on the correlation length. 
-  % need citations and more on Lorentzian parameters
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}	
-  	\includegraphics[width=\textwidth]{waxs_dashed.png}
-	\caption{}~\label{fig:waxs_dashed}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
-	\caption{}~\label{fig:correlation_length_exp}
-  \end{subfigure}
-  \caption{(a) We estimated the system's experimental correlation length using a 
-  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a Lorentzian curve 
-  to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
-  The correlation length is 1/FWHM.}~\label{fig:correlation}
-  \end{figure}
-  \vspace{1em} \\
+  \clearpage
+%  \section{Experimental correlation length of R-$\pi$}\label{section:correlation_length}
+% 
+%  \vspace{1em}
+%  Previous experimental studies of these systems did not calculate the correlation length, so we estimated it
+%  from the raw 2D WAXS data. We took a slice of the 2D WAXS data along the dashed line in
+%  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
+%  intensity far from the pattern (high $q$) uniformly. We used a least squares
+%  algorithm to fit a Lorentzian curve to the data. Only values recorded above
+%  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
+%  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
+%  maximum (FWHM) is related to the correlation length, L, by the relationship: $
+%  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
+%  of the diagonal entry of the covariance matrix of optimized fit parameters.
+%  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
+%  method. Since the experimental peak width is also influenced by strain and 
+%  instrumental broadening in addition to finite size broadening, the value 
+%  calculated here is really only an upper bound on the correlation length. 
+%  % need citations and more on Lorentzian parameters
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}	
+%  	\includegraphics[width=\textwidth]{waxs_dashed.png}
+%	\caption{}~\label{fig:waxs_dashed}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
+%	\caption{}~\label{fig:correlation_length_exp}
+%  \end{subfigure}
+%  \caption{(a) We estimated the system's experimental correlation length using a 
+%  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a Lorentzian curve 
+%  to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
+%  The correlation length is 1/FWHM.}~\label{fig:correlation}
+%  \end{figure}
+%  \vspace{1em} \\
+
+  \section{Component radial density functions}\label{section:radial_density}
 
@@
   \end{figure}
-
+  \clearpage
+
+  \begin{figure}
+  \begin{minipage}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{monomer_color_coded.png}
+  \vspace{4.5em}
+  \caption{The groups used for radial distribution calculations. Red atoms are in the
+  tails group. Green atoms are in the head group region. The blue atom is sodium.}\label{fig:monomer_color_coded}
+  \end{minipage}\qquad
+  \begin{minipage}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{radial_distribution_annulus.png}
+  \caption{
+  Looking down onto the plane of membrane, 
+  % this diagram
+  % illustrates how we calculated radial distribution
+  % functions.
+  we binned the radial distance of all atoms in chosen groups from
+  pore centers. The bins are defined by the annulus bounded by concentric
+  circles centered at the pore centers, as shown. We normalize by
+  dividing the count of atoms within each bin annulus by its volume.
+%  of
+%  the annulus where the volume is the area of the annulus times the
+%  height of the membrane in the z-direction.
+  }~\label{fig:rdf_diagram}
+  \end{minipage}
+  \end{figure}
 % BJC: Unnecessary, supporting info already long
@@
   Figure~\ref{fig:tail_sections}.
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{tail_sections.png}
+  \caption{We divided the tail into three regions: tail-fronts (blue), 
+  tail-middles (green) and tail-backs (red).}\label{fig:tail_sections}
+  \end{figure}
 
@@
         \centering
-  \includegraphics[width=0.5\textwidth]{tail_sections}
-  \caption{We divided the tail into three regions: tail-fronts (blue), 
-  tail-middles (green) and tail-backs (red).}\label{fig:tail_sections}
-  \end{figure}
-
-  \begin{figure}[!htb]
-        \centering
         \begin{subfigure}{0.45\textwidth}
@@
 
-  \begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.75\linewidth]{radial_distribution_annulus.png}
-	\caption{Looking down onto the plane of membrane, this diagram
-		illustrates how we calculated radial distribution
-		functions. We binned the radial distance of all atoms in 
-                chosen groups from pore centers. The pore centers are 
-                defined as the average coordinates of sodium ions in each
-                pore. The bins are defined by the annulus bounded by concentric
-		circles centered at the pore centers, as shown. To normalize, we
-		divide the count of atoms within the bin annulus by the volume of
-                the annulus where the volume is the area of the annulus times the
-                height of the membrane in the z-direction.}~\label{fig:rdf_diagram}
-  \end{figure}
+  \clearpage
+
+  \section{Diffusion of monomers}
+
+  We calculated the diffusion coefficient of the monomer head groups by measuring
+  the slope of the linear region of their mean squared displacement curves accumulated
+  over the length of the equilibration simulations (Table~\ref{table:msd}).
 
@@
   \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
-  which is three orders of magnitude lower than literature values.}~\label{table:msd}
+  .}~\label{table:msd}
   \end{table}
 
-  \begin{figure}[!htb]
-  \centering
-        \begin{subfigure}{0.45\textwidth}
-                \includegraphics[width=\textwidth]{water_filled_pore.png}
-                \caption{}\label{fig:water_filled_pores}
-        \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-                \includegraphics[width=\textwidth]{water_removed.png}
-                \caption{}\label{fig:water_removed}
-        \end{subfigure}
-  \caption{(a) Pores built in the parallel displaced configuration with 5
-	  monomers per layer are filled with 5 wt\% water. (b) The same system is
-	  visualized with water molecules and sodium ions removed. Head groups vacate the
-	  pore region leaving an aqueous solution of water and sodium ions.}\label{fig:water_pores}
-  \end{figure}
-
-  \section{Demonstrative Fourier transforms}\label{section:fourier}
-
-  Here we use Fourier transforms to demonstrate some of the arguments made in 
-  the main text. Interpretation of real and simulated X-ray diffraction patterns
-  is non-trivial and requires careful thought. They are a function of the positions
-  of all atoms in space, and suffer from the phase problem. Namely, there are multiple
-  solutions that could explain a single diffraction pattern. Using simplified models, 
-  we can hypothesize about the effect of various configurations on the simulated patterns.
-
-  \subsection{Magnitude of R-$\pi$}\label{section:rpi_ft}
-
-  In all cases, the magnitude of R-$\pi$ in our system is larger than that in experiment.
-  Some of the discrepancy can be explained by defects and imperfect pore alignment. 
-  However, there are significant effects resulting from the ordered states that we simulate.
-
-  Persistent oscillations in the z-correlation function, $g(z)$, increase the intensity of R-$\pi$. 
-  In Figure~\ref{fig:z_correlation}, we fit a decaying sinusoidal function 
-  (equation~\ref{M-eqn:decaying_sinusoid} of the main text) to $g(z)$ calculated from the
-  sandwiched configuration in the ordered basin. While the sinusoidal decay fit decays to one
-  rather quickly, $g(z)$ continues to oscillate with nearly the same amplitude as its third peak. 
-  In Figure~\ref{fig:theoretical_correlation_functions}, we overlay the same decaying sinusoidal
-  fit with a function that continues to oscillate with the same amplitude as the third peak of
-  the fit to $g(z)$. In Figure~\ref{fig:power_spectrum_comparison}, we plot the power spectrum
-  generated from the discrete Fourier transform of the plots in Figure~\ref{fig:theoretical_correlation_functions}. 
-  The maximum intensity of the power spectrum increases by nearly 60\% when the correlation 
-  function does not decay to one. This explains, in part, the large simulated value of the
-  intensity of R-$\pi$.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{z_correlation_layered_sinefit.png}
-  \caption{}\label{fig:z_correlation}
-  \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{theoretical_correlation_functions.png}
-  \caption{}\label{fig:theoretical_correlation_functions}
-  \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{power_spectrum_comparison.png}
-  \caption{}\label{fig:power_spectrum_comparison}
-  \end{subfigure}
-  \caption{(a) We fit a decaying sinusoidal function to the z-correlation function, $g(z)$, 
-  calculated from the ordered basin sandwiched system. The oscillations in $g(z)$ continue
-  to oscillate at nearly the same amplitude as its third peak. (b) We overlaid a plot of the
-  fit to $g(z)$ with a similar function that continues to oscillate with the same amplitude
-  as its third peak. (c) The power spectrum of each plot in (b) exhibits a 60\% increase in
-  intensity of the peaks when the function does not decay to 1.}\label{fig:rpi_ft}
-  \end{figure}
-
-  \subsection{Simplified assemblies}\label{section:simplified_assemblies}
-
-  We explored the sandwiched and parallel displaced configurations as potential ways for
-  aromatic head groups to stack. We used copies of the same monomer to build each system.
-  We were unable to create any assemblies which exhibited R-double using this technique. 
-  We simulated diffraction patterns of simplified configurations to understand why. We 
-  placed points in array that resemble the sandwiched and parallel displaced configurations.
-  Points are space 3.7 $\AA$ apart so it is easy to relate them to LLC membrane system.
-  5 columns of points are placed 5 $\AA$ from a defined "pore center".
-
-  When points are stacked in either configuration, R-double cannot appear. In the case
-  of the sandwiched configuration, the fundamental frequency is set at 1.7 $\AA^{-1}$,
-  the same location as R-$\pi$. Subharmonics appear at integer multiples of this frequency.
-  The parallel displaced configuration exhibits reflections at half the $q_z$ value of
-  R-$\pi$, which is where we expect to see R-double. However, just like the LLC membrane
-  system, the reflections appear away from $q_r=0$ and are caused by the helical stacking
-  arrangement.
-
-  From these observations, it is clear that, in order to make R-double appear in our simulated
-  diffraction patterns, we must create systems with asymmetries along the z-axis which lead to
-  a fundamental frequency of $0.85 \AA^{-1}$. This requires a modulation in electron density 
-  every 7.4 $\AA$. This line of thought gave rise to the systems studied in 
-  section~\ref{M-section:rdouble} of the main text.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{simple_sandwich_realspace.png}
-  \caption{}\label{fig:simple_sandwich_realspace}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{simple_sandwich_rzplot.png}
-  \caption{}\label{fig:simple_sandwich_rzplot}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{simple_offset_realspace.png}
-  \caption{}\label{fig:simple_offset_realspace}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{simple_offset_rzplot.png}
-  \caption{}\label{fig:simple_offset_rzplot}
-  \end{subfigure}
-  \caption{}\label{fig:simple_FTs}
-  \end{figure}
-
-  \section{Solvation}\label{section:solvation}
+% BJC: not necessary
+%  \begin{figure}[!htb]
+%  \centering
+%        \begin{subfigure}{0.45\textwidth}
+%                \includegraphics[width=\textwidth]{water_filled_pore.png}
+%                \caption{}\label{fig:water_filled_pores}
+%        \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+%                \includegraphics[width=\textwidth]{water_removed.png}
+%                \caption{}\label{fig:water_removed}
+%        \end{subfigure}
+%  \caption{(a) Pores built in the parallel displaced configuration with 5
+%	  monomers per layer are filled with 5 wt\% water. (b) The same system is
+%	  visualized with water molecules and sodium ions removed. Head groups vacate the
+%	  pore region leaving an aqueous solution of water and sodium ions.}\label{fig:water_pores}
+%  \end{figure}
+
+% BJC: a lot of this is in the main text, but there is some other potentially usefull stuff in here
+%  \section{Demonstrative Fourier transforms}\label{section:fourier}
+%  
+%  Here we use Fourier transforms to demonstrate some of the arguments made in 
+%  the main text. Interpretation of real and simulated X-ray diffraction patterns
+%  is non-trivial and requires careful thought. They are a function of the positions
+%  of all atoms in space, and suffer from the phase problem. Namely, there are multiple
+%  solutions that could explain a single diffraction pattern. Using simplified models, 
+%  we can hypothesize about the effect of various configurations on the simulated patterns.
+%
+%  \subsection{Magnitude of R-$\pi$}\label{section:rpi_ft}
+%  
+%  In all cases, the magnitude of R-$\pi$ in our system is larger than that in experiment.
+%  Some of the discrepancy can be explained by defects and imperfect pore alignment. 
+%  However, there are significant effects resulting from the ordered states that we simulate.
+%  
+%  Persistent oscillations in the z-correlation function, $g(z)$, increase the intensity of R-$\pi$. 
+%  In Figure~\ref{fig:z_correlation}, we fit a decaying sinusoidal function 
+%  (equation~\ref{M-eqn:decaying_sinusoid} of the main text) to $g(z)$ calculated from the
+%  sandwiched configuration in the ordered basin. While the sinusoidal decay fit decays to one
+%  rather quickly, $g(z)$ continues to oscillate with nearly the same amplitude as its third peak. 
+%  In Figure~\ref{fig:theoretical_correlation_functions}, we overlay the same decaying sinusoidal
+%  fit with a function that continues to oscillate with the same amplitude as the third peak of
+%  the fit to $g(z)$. In Figure~\ref{fig:power_spectrum_comparison}, we plot the power spectrum
+%  generated from the discrete Fourier transform of the plots in Figure~\ref{fig:theoretical_correlation_functions}. 
+%  The maximum intensity of the power spectrum increases by nearly 60\% when the correlation 
+%  function does not decay to one. This explains, in part, the large simulated value of the
+%  intensity of R-$\pi$.
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.32\textwidth}
+%  \includegraphics[width=\textwidth]{z_correlation_layered_sinefit.png}
+%  \caption{}\label{fig:z_correlation}
+%  \end{subfigure}
+%  \begin{subfigure}{0.32\textwidth}
+%  \includegraphics[width=\textwidth]{theoretical_correlation_functions.png}
+%  \caption{}\label{fig:theoretical_correlation_functions}
+%  \end{subfigure}
+%  \begin{subfigure}{0.32\textwidth}
+%  \includegraphics[width=\textwidth]{power_spectrum_comparison.png}
+%  \caption{}\label{fig:power_spectrum_comparison}
+%  \end{subfigure}
+%  \caption{(a) We fit a decaying sinusoidal function to the z-correlation function, $g(z)$, 
+%  calculated from the ordered basin sandwiched system. The oscillations in $g(z)$ continue
+%  to oscillate at nearly the same amplitude as its third peak. (b) We overlaid a plot of the
+%  fit to $g(z)$ with a similar function that continues to oscillate with the same amplitude
+%  as its third peak. (c) The power spectrum of each plot in (b) exhibits a 60\% increase in
+%  intensity of the peaks when the function does not decay to 1.}\label{fig:rpi_ft}
+%  \end{figure}
+%  
+%  \subsection{Simplified assemblies}\label{section:simplified_assemblies}
+%  
+%  We explored the sandwiched and parallel displaced configurations as potential ways for
+%  aromatic head groups to stack. We used copies of the same monomer to build each system.
+%  We were unable to create any assemblies which exhibited R-double using this technique. 
+%  We simulated diffraction patterns of simplified configurations to understand why. We 
+%  placed points in array that resemble the sandwiched and parallel displaced configurations.
+%  Points are space 3.7 $\AA$ apart so it is easy to relate them to LLC membrane system.
+%  5 columns of points are placed 5 $\AA$ from a defined "pore center".
+%  
+%  When points are stacked in either configuration, R-double cannot appear. In the case
+%  of the sandwiched configuration, the fundamental frequency is set at 1.7 $\AA^{-1}$,
+%  the same location as R-$\pi$. Subharmonics appear at integer multiples of this frequency.
+%  The parallel displaced configuration exhibits reflections at half the $q_z$ value of
+%  R-$\pi$, which is where we expect to see R-double. However, just like the LLC membrane
+%  system, the reflections appear away from $q_r=0$ and are caused by the helical stacking
+%  arrangement. 
+%  
+%  From these observations, it is clear that, in order to make R-double appear in our simulated
+%  diffraction patterns, we must create systems with asymmetries along the z-axis which lead to
+%  a fundamental frequency of $0.85 \AA^{-1}$. This requires a modulation in electron density 
+%  every 7.4 $\AA$. This line of thought gave rise to the systems studied in 
+%  section~\ref{M-section:rdouble} of the main text.
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{simple_sandwich_realspace.png}
+%  \caption{}\label{fig:simple_sandwich_realspace}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{simple_sandwich_rzplot.png}
+%  \caption{}\label{fig:simple_sandwich_rzplot}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{simple_offset_realspace.png}
+%  \caption{}\label{fig:simple_offset_realspace}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{simple_offset_rzplot.png}
+%  \caption{}\label{fig:simple_offset_rzplot}
+%  \end{subfigure}
+%  \caption{}\label{fig:simple_FTs}
+%  \end{figure}
+
+  \section{All solvated systems}\label{section:solvation}
 
@@
 
+  \section{The role of water in the appearance of R-double}\label{section:rdouble}
+
+  The appearance of R-double is likely a consequence of structure induced when
+  vertically stacked monomer pairs share hydrogen bonds with a common water molecules (See
+  Section~\ref{M-section:rdouble} of the main text). We quantified the occurence of
+  these pairing interactions by binning the $z$-positions of the center of mass of 
+  the monomer head groups into 20 bins, the same number as the monomers per column. 
+  This works relatively well since there is a high degree of correlation between
+  columns in our system. Peaks in the distributions represent the scenario where a monomer head group
+  shares a water molecule with a head group vertically above it (See Figure~\ref{fig:pore_hbonds}).
+  We calculated the discrete Fourier transform of the distributions in Figure~\ref{fig:pore_hbonds}
+  which we used as a rough indicator of whether the head group arrangement will lead to R-double
+  (Figure~\ref{fig:pore_hbonds_ft}). We see the strongest indicator of asymmetric monomer
+  stacking in Pore 1 where the peaks at 0.75 $\AA^{-1}$ are clearly distinguishable, meaning
+  there is periodicity at twice the $\pi$-stacking distance.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{pore_hbonds.png}
+  \caption{}\label{fig:pore_hbonds}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
+  \caption{}\label{fig:pore_hbonds_ft}
+  \end{subfigure}
+  \caption{(a) We group the $z$-coordinate of the center of mass of monomer
+  head groups into 20 bins. Peaks in the distributions indicate a shared hydrogen bonded
+  water molecule between a monomer head group and one in the bin vertically above it. 
+  The distance between the peaks roughly corresponds to the distance between pairs of 
+  monomers. The distance between peaks in pore 1 (indicated by arrows) is equal to two 
+  times the $\pi$-stacking distance. In this scenario, monomers are no longer evenly spaced
+  in the $z$-direction since they are pulled closer together by hydrogen bonds. (b) We 
+  performed discrete Fourier transforms on each distribution in (a) In Pore 1, there 
+  is periodicity every 8.3 $\AA$, twice the $\pi$-stacking distance, as indicated by the
+  intensity at 0.76 $\AA^{-1}$. In this case, the center of mass of two adjacent pairs 
+  is separated by twice the average monomer stacking distance, while the four monomers 
+  involved are unequally spaced. These conditions seem likely to give rise to R-double.
+  }\label{fig:hbonds}
+  \end{figure}
+
   \section{Crosslinking algorithm details}\label{section:xlink}
 
-  Crosslinking of the the monomer Na-GA3C11 occurs by a UV initiated free
+  Crosslinking of the the monomer Na-GA3C11 occurs via a UV initiated free
   radical polymerization (FRP) (Figure~\ref{fig:xlink_mech}). Head-to-tail addition
@@
 	  radical initiators to create monomers with terminal vinyl radicals.  Vinyl
-	  radicals react with the vinyl groups of other monomers in to propagate
+	  radicals react with the vinyl groups of other monomers in order to propagate
 	  crosslinking.}\label{fig:xlink_mech}
@@
   to readjust. For those reasons we did not cross-link all systems tested.
+
+  \clearpage
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{z_correlation_overlay.png}
-  \caption{The correlation functions generated from ordered basin sandwiched configurations
-  with different z-dimensions. The correlation function is nearly the same when the z-dimension
-  of the system is doubled.}\label{fig:z_correlation_overlay}
-  \end{figure}
-
-  \begin{figure}[!htb]
-  \centering
   \includegraphics[width=0.5\textwidth]{carboxylate_dihedral_rb.png}
@@
 %  \end{figure}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{monomer_dihedrals.png}
+  \caption{We measured the autocorrelation functions of the dihedrals highlighted in
+  black. We only included dihedrals associated with the outer tails in our calculation
+  since the position of the center tail leads to fundamentally different interactions and
+  dynamics.}\label{fig:dihedrals}
+  \end{figure}
 

### 2018-08-28 Ben_Manuscripts/structure_paper/Draft.tex
Updates to the introduction

@@
 
-  %MRS13: I tweaked this a bit.  Probably could add another sentence to add some of the other important findings.
-  Nanostructured porous membranes made from the cross-linked hexagonal phase of
-  self-assembled lyotropic liquid crystals (LLCs) are a promising material for
-  selective separations. In this work, we investigate an experimentally
-  characterized LLC membrane using atomistic molecular modeling. In particular, we compare
-  simulated X-ray diffraction (XRD) patterns with experimental XRD to quantify and understand 
-  differences between simulation and experiment.
-  We find that pores are
-  likely composed of 5 columns of stacked LLC monomers which surround each
-  hydrophilic core.  We also find that some of the structure previously attributed to 
-  monomer tail tilt is likely instead due to ordered tail packing.  
-  Although this system has been reported as dry, we show that
-  small amounts of water are necessary to fully reproduce the experimental XRD
-  pattern due to asymmetries introduced by hydrogen bonds between monomer head
-  groups and water molecules. We explore the composition and structure of the
-  nanopores and reveal that there exists a composition gradient rather than a
-  abrupt partition between the hydrophilic and hydrophobic regions. A caveat is
-  that the time scales of the dynamics are extremely long for this system, resulting in 
-  simulated structures that appear too ordered, 
-  %MRS13: I left out starting from alternative structures since we didn't actually do it.
-  %requiring starting from a range of alternative initial configurations and
-  and requiring careful examination of the metastable states observed for any conclusions. The clearer picture of
-  the nanoscopic structure of these membranes provided in this study will enable
-  a better understanding of the mechanisms of small molecule transport within
-  these nanopores.
+  Nanostructured porous membranes made from the cross-linked hexagonal phase
+  of self-assembled lyotropic liquid crystals (LLCs) are a promising material
+  for selective separations. In this work, we investigate an experimentally
+  characterized LLC membrane using atomistic molecular modeling. In particular,
+  we compare simulated X-ray diffraction (XRD) patterns with experimental XRD
+  to quantify and understand the differences between simulation and experiment.
+  We find that pores are likely composed of 5 columns of stacked LLC monomers
+  which surround each hydrophilic core. We learned that these columns likely 
+  move independently of each other over time scales which we can not simulate.
+  We find that some of the structure previously attributed to monomer tail 
+  tilt is likely instead due to ordered tail packing. Although this system
+  has been reported as dry, we show that small amounts of water are necessary
+  to fully reproduce all features from the experimental XRD pattern due to
+  asymmetries introduced by hydrogen bonds between monomer head groups and
+  water molecules. We explore the composition and structure of the nanopores
+  and reveal that there exists a composition gradient rather than an abrupt
+  partition between the hydrophilic and hydrophobic regions. 
+  % BJC13: If this is to be included here, it needs some rewording. I allude to
+  % this when talking about the independently moving columns above. 
+  %A caveat is
+  %that the time scales of the dynamics are extremely long for this system, 
+  %resulting in simulated structures that appear too ordered which requires
+  %careful examination of the metastable states observed in order to draw any
+  %conclusions. 
+  The clearer picture of the nanoscopic structure of these membranes provided
+  in this study will enable a better understanding of the mechanisms of small
+  molecule transport within these nanopores.
+
   \end{abstract}
@@
 
-  More highly selective membranes would be extremely useful for the recovery of
-  dissolved species in complex aqueous and organic solutions. For example,
-  selective membranes can further progress forward osmosis processes by reducing
-  the cost of separating potable water from draw
-  solutions~\cite{mccutcheon_novel_2005}. Additionally, flowback water (FW)
-  produced during hydraulic fracturing is a complex wastewater full of
-  potentially valuable dissolved organic compounds such as acetate that can be
-  recovered using highly selective membranes \cite{dischinger_application_2017}.
-  Finally, a significant amount of nitrogen and phosphorus from fertilizer is
-  found in wastewater. Selective membranes offer a route towards low energy
-  nutrient recovery from these wastewaters which can help sustain fertilizer
-  production and subsequently food production into the future
-  \cite{xie_membrane-based_2016}.
+  More highly selective membranes would be extremely useful for both the
+  recovery of valuable dissolved species from and the purification of complex
+  aqueous solutions. The supply of fresh water is being increasingly strained
+  by population growth, industrialization and climate change
+  \cite{elimelech_future_2011}. Consequently, people are turning towards
+  treatment of unconventional water sources such as seawater and wastewater. 
+  In addition to obtaining fresh water from them, these water sources, 
+  particularly municipal and industrial wastewater, have been found to contain 
+  valuable resources which can be separated using highly selective membranes~\cite{sales_resource_2015}.
+
+  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane 
+  filtration processes that can be used to separate solutes on the order of 1 
+  nm in size and smaller, as well as ions. Both apply hydraulic pressure to 
+  the feed solution in order to overcome osmotic pressure and force water
+  and unfiltered components through the membrane. RO membranes typically have
+  a thin film composite architecture which, at minimum, consists of a porous
+  support layer and a dense polymer active layer. Separation occurs based on the differences in
+  solubility and diffusivity of feed solution constituents with respect to the
+  active layer. Nanofiltration membranes have explicit pores on the order of 1
+  nm in diameter which are typically tortuous and polydisperse in size. They 
+  separate primarily based on size exclusion as well as Donnan exclusion if the
+  membrane has a surface charge~\cite{van_der_bruggen_review_2003}.
+
+  The energy consumed during the purification of seawater and wastewater 
+  using RO and NF membranes can be reduced by increasing their selectivity 
+  towards water \cite{werber_materials_2016}. While researchers often focus on
+  improving membrane permeability, the flux of water through a given membrane,
+  it has been shown that increased water permeability only slightly decreases
+  energy requirements \cite{cohen-tanugi_quantifying_2014}.
+%  since the main energy requirement for a membrane separation is that needed
+%  to create the hydraulic pressure necessary in order to overcome the 
+%  osmotic pressure of the feed solution\cite{cohen-tanugi_quantifying_2014}. 
+  Often times, multiple membrane passes are required in order to sufficiently
+  reduce contaminant levels. For example, boric acid is toxic to humans and 
+  is present in seawater at levels well above acceptable drinking standards.
+  It is difficult to sufficiently separate boric acid in a single pass, meaning
+  multiple passes are needed and energy requirements nearly double \cite{fritzmann_state---art_2007}.
+%  This is necessary in the case where high-purity water
+%  is needed \cite{singh_production_2009}, when separating small neutral solutes \cite{ozaki_rejection_2002} or
+%  when removing boric acid from seawater \cite{fritzmann_state---art_2007}.  
+  The most effective way to reduce energy consumption
+  would be to reduce the number of membrane passes for a given system using 
+  more selective membranes. 
+%   More highly selective membranes have the potential
+%  to reduce the number of membrane passes in addition to eliminating the need 
+%  for other post-treatment steps necessitated by incomplete separations.
+  %dissolved species which negatively
+%  affect human health.
+
+  Not only will increased selectivity reduce the energy consumption of membrane
+  processes, but it offers a way to recover valuable resources from the feed 
+  streams. Municipal and industrial wastewaters are contaminated by harmful
+  micropollutants, but also contain valuable dissolved solutes. Micropollutants include
+  pharmaceutical and personal care products, hormones, pesticides and industrial
+  chemicals, all of which have adverse effects on human health even at low 
+  concentrations\cite{schwarzenbach_challenge_2006}. A selective membrane has the % There is a need for membranes
+  potential to reject these components while still allowing the passage of valuable 
+  resources for further processing and recovery.
+
+  Municipal wastewaters are rich in carbon, nitrogen and phosphorus-containing 
+  compounds. The recovery of such products, which can be achieved using a 
+  selective membrane, has numerous potential uses \cite{sales_resource_2015}. 
+  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
+  production which will help meet global food demand as population continues
+  to increase \cite{xie_membrane-based_2016}.
+
+  Industrial waste-waters are often quite complex with up to six times more 
+  total dissolved solids than seawater\cite{werber_materials_2016}. For example, flowback water, produced
+  during hydraulic fracturing of shale formations consists of relatively high
+  concentrations of salts, metals, and soluble organic compounds. The majority
+  of this water is disposed through deep well injection, however there is a growing public concern about
+  its management which has prompted the use of separation technologies such as 
+  RO and NF in order to reduce the volume of contaminated water~\cite{gregory_water_2011}.
+  Some of the dissolved organic compounds in flowback water, such as acetate, 
+  are potentially valuable and can be recovered with highly selective membranes
+  ~\cite{dischinger_application_2017}.
+
+%  More highly selective membranes would be extremely useful for the recovery of
+%  dissolved species in complex aqueous and organic solutions. For example,
+%  selective membranes can further progress forward osmosis processes by reducing
+%  the cost of separating potable water from draw
+%  solutions~\cite{mccutcheon_novel_2005}. Additionally, flowback water (FW)
+%  produced during hydraulic fracturing is a complex wastewater full of
+%  potentially valuable dissolved organic compounds such as acetate that can be
+%  recovered using highly selective membranes \cite{dischinger_application_2017}.
+%  Finally, a significant amount of nitrogen and phosphorus from fertilizer is
+%  found in wastewater. Selective membranes offer a route towards low energy
+%  nutrient recovery from these wastewaters which can help sustain fertilizer
+%  production and subsequently food production into the future
+%  \cite{xie_membrane-based_2016}.
   % as we near peak production of minable phosphorus rock .
@@
 
-% MRS6: I would keep a paragraph about here how current membranes DON'T
-% work for this purpose. But one paragraph is enough.
-% BJC5: added back below paragraph.  
-% MRS8: ``because they are unstructured'' lacks detail.  NF has some structure, since there are irregular pores. Check some other reviews and see the points they cover?
   Current commercial RO and NF membranes suffer limitations to their selectivity
-  because they are unstructured. Although scalable, their fabrication involves the 
-  spontaneous assembly of polymers into disordered structures which offer separation 
-  pathways that are tortuous and polydisperse in size. This makes overcoming the well-known 
-  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
-  the permeability of a desired molecular or atomic species, while maintaining the 
-  same retention of an undesired species \cite{werber_materials_2016}.
+  because their structures incorporate some degree of randomness. Although scalable, their 
+  fabrication involves the spontaneous assembly of polymers into disordered structures
+  which offer separation pathways that are tortuous and polydisperse in size 
+  \cite{werber_materials_2016}. Tortuosity increases the effective length that a 
+  solute must travel, while polydispersity limits membrane selectivity.
+
+%BJC13: You can stop here, I haven't changed anything below.
+
+%  This makes overcoming the well-known 
+%  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
+%  the permeability of a desired molecular or atomic species, while maintaining the 
+%  same retention of an undesired species \cite{werber_materials_2016}.
 
@@
   we used the $q_r$ cross-section of 2D SAXS which was generated from the same
-  sample (Figure S-TBD). Since the d\textsubscript{110} peak is
-  %BJC12: verify which crystal plane it is.  
+  sample (Figure S-\ref{S-fig:2DSAXS}). Since the d\textsubscript{200} peak is
   partially exposed in the experimental 2D WAXS pattern, we normalized the
   experimental 2D SAXS cross-section by matching the intensity of the
-  d\textsubscript{110} peak between it and the experimental 2D WAXS
+  d\textsubscript{200} peak between it and the experimental 2D WAXS
   cross-section. It is possible that the peak is not fully captured in the 2D
@@
   modest number of occurrences of this scenario, which we quantify in further
-  detail in the Supporting Information, Section S-TBD.
+  detail in the Supporting Information, Section S-\ref{S-section:rdouble}.
 

### 2018-08-28 Ben_Manuscripts/structure_paper/supporting_information.tex
Updates to the introduction

@@
 
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{2DSAXS_axes.png}
+  \caption{Two dimensional small angle X-ray scattering experiments show
+  reflections along the $q_r$ axis at $q_z$=0. The spacing between the reflections
+  is characteristic of a hexagonal phase and is directly related to the distance
+  between pores. The reflections are arced because the pores are not perfectly
+  aligned. A perfectly aligned system would show dots at each peak location. An
+  isotropically aligned system would show concentric rings about the origin which
+  pass through each peak location. The d\textsubscript{100} and d\textsubscript{110} 
+  peaks (the first two pairs of reflections from origin located at $|\mathbf{q}| 
+  \approx 0.18~\AA^{-1}$ and $|\mathbf{q}| \approx 0.31~\AA^{-1}$) are not visible
+  in the 2D WAXS pattern. The edges of the d\textsubscript{200} reflection (the third
+  pair of reflections located at $|\mathbf{q}| \approx 0.36~\AA^{-1}$) are slightly
+  visible in the 2D WAXS pattern, so we used them to approximate the experimental
+  intensity of R-pores.}\label{fig:2DSAXS}
+  \end{figure}
+
 \clearpage

### 2018-08-29 Ben_Manuscripts/structure_paper/Draft.tex
some thoughts on intro and abstract.

@@
   %conclusions. 
+  %MRS14: OK, let's talk through it.  I feel that this is an important caveat to add so
+  %that people don't think we are claiming more than we are, and therefor should be mentioned
+  % explicitly, rather than the implication left above.
   The clearer picture of the nanoscopic structure of these membranes provided
@@
 
+  %MRS14: I feel this introduction spends a bit too much time talking at too general a level.
+The paper introduction to the problem tackled in the paper.
+One simple way to tighten it up would be to improve the connection between the thesis and the data.
+You say that highly selective membranes would be useful, but then don't provide evidence that they are the solution to the problems listed.
   More highly selective membranes would be extremely useful for both the
@@
   support layer and a dense polymer active layer. Separation occurs based on the differences in
-  solubility and diffusivity of feed solution constituents with respect to the
+  solubility and diffusivity of feed solution constituents 
+  %MRS14:
+  %with respect to the
+  in the 
   active layer. Nanofiltration membranes have explicit pores on the order of 1
@@
 
+  %MRS14: is selectivity towards water important, or selectivity against what one wants filtered out?
   The energy consumed during the purification of seawater and wastewater 
@@
   Often times, multiple membrane passes are required in order to sufficiently
+  %MRS14: not sure the boric acid part is that relevant, since we don't really talk about 
+  %that in the rest of the paper.
   reduce contaminant levels. For example, boric acid is toxic to humans and 
@@
 
+  %MRS14: could possibly be food details, if selective membranes are the key to purifying industrial waste waters. 
   Industrial waste-waters are often quite complex with up to six times more 

### 2018-08-29 Ben_Manuscripts/structure_paper/Draft.tex
updates
reworked intro

@@
 You say that highly selective membranes would be useful, but then don't provide evidence that they are the solution to the problems listed.
-  More highly selective membranes would be extremely useful for both the
-  recovery of valuable dissolved species from and the purification of complex
-  aqueous solutions. The supply of fresh water is being increasingly strained
-  by population growth, industrialization and climate change
-  \cite{elimelech_future_2011}. Consequently, people are turning towards
-  treatment of unconventional water sources such as seawater and wastewater. 
-  In addition to obtaining fresh water from them, these water sources, 
-  particularly municipal and industrial wastewater, have been found to contain 
-  valuable resources which can be separated using highly selective membranes~\cite{sales_resource_2015}.
+
+  % In order to perform complex separations x, y and z at reduced costs, we need highly selective membranes 
+  % include all descriptions of separation processes into this paragraph
+
+  More highly selective nanoporous membranes would be extremely useful in order
+  to perform complex aqeuous separations with seawater and various sources of
+  wastewater. Sodium chloride and boron in seawater, and organic micropollutants
+  found in municipal and industrial wastewaters are a few examples of the
+  diversity of components that make up various water sources. By efficiently
+  separating contaminants from feed solutions with highly selective membranes,
+  one can reduce the number of required membrane passes and post-treatment steps,
+  thus lowering the energy requirements of the separation processes.
+  Additionally, one can extract valuable resources from the feed streams. For
+  example, flowback water produced during hydraulic fracturing of shale
+  formations contains dissolved species such as acetate whose extraction could be
+  economically valuable.
+
+% More highly selective membranes would be extremely useful for both the
+% recovery of valuable dissolved species from and the purification of complex
+%  aqueous solutions. The supply of fresh water is being increasingly strained
+%  by population growth, industrialization and climate change
+%  \cite{elimelech_future_2011}. Consequently, people are turning towards
+%  treatment of unconventional water sources such as seawater and wastewater. 
+%  In addition to obtaining fresh water from them, these water sources, 
+%  particularly municipal and industrial wastewater, have been found to contain 
+%  valuable resources which can be separated using highly selective membranes~\cite{sales_resource_2015}.
+  % make possible with selectively permeable membranes -- better than thermal distillation
+
+ % (2) existing nanoporous membranes + drawbacks
 
   Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
-  filtration processes that can be used to separate solutes on the order of 1 
-  nm in size and smaller, as well as ions. Both apply hydraulic pressure to 
-  the feed solution in order to overcome osmotic pressure and force water
-  and unfiltered components through the membrane. RO membranes typically have
-  a thin film composite architecture which, at minimum, consists of a porous
-  support layer and a dense polymer active layer. Separation occurs based on the differences in
-  solubility and diffusivity of feed solution constituents 
-  %MRS14:
-  %with respect to the
-  in the 
-  active layer. Nanofiltration membranes have explicit pores on the order of 1
-  nm in diameter which are typically tortuous and polydisperse in size. They 
-  separate primarily based on size exclusion as well as Donnan exclusion if the
-  membrane has a surface charge~\cite{van_der_bruggen_review_2003}.
+  filtration processes that can be used to separate solutes on the order of 1 nm
+  in size and smaller, as well as ions, however the porous architecture of
+  commercially dominant membranes lack uniformity which severely impacts their
+  selectivity. Although scalable, their fabrication involves the spontaneous
+  assembly of polymers into disordered structures which offer separation pathways
+  that are tortuous and polydisperse in size \cite{werber_materials_2016}.
+  Tortuosity increases the effective length that a solute must travel, while
+  polydispersity limits membrane selectivity.
+
+  % (3) justification for why nanostructured membranes are a good idea for this
+  % long-term route towards highly selective membranes are those that are nanostructured
+  Nanostructured porous membrane materials have become increasingly popular for
+  aqueous separations applications because they offer the ability to control pore
+  architecture at the molecular scale, thereby permitting the design of
+  solute-specific separation membranes \cite{humplik_nanostructured_2011},
+  however their development has been limited by the ability to synthesize and
+  scale various fundamentally sound technologies. Graphene sheets are atomically
+  thick which results in excellent water permeability but defects during
+  manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
+  Molecular dynamics (MD) simulations of carbon nanotubes show promise
+  \cite{humplik_nanostructured_2011}, but synthetic techniques are unable to
+  achieve scalable alignment and pore monodispersity
+  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Consequently, there is a
+  need for a scalable nanostructured porous membrane.
+
+%BJC14: zeolites aren't really nanostructured
+% Zeolites have sub-nm
+%  pores with a narrow pore size distribution, and MD simulations of these
+%  materials show that they exhibit complete rejection of solvated ions
+%  \cite{murad_molecular_1998}- however, experimental rejection was low and
+%  attributed to interstitial defects formed during membrane synthesis
+%  \cite{li_desalination_2004}.
+
+  % (4) justify LLCs
+
+  % (5) justify need for simulations
+
+%  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
+%  filtration processes that can be used to separate solutes on the order of 1 nm
+%  in size and smaller, as well as ions. Both apply hydraulic pressure to the feed
+%  solution in order to overcome osmotic pressure and force water and unfiltered
+%  components through the membrane. RO membranes typically have a thin film
+%  composite architecture which, at minimum, consists of a porous support layer
+%  and a dense polymer active layer. Separation occurs based on the differences in
+%  solubility and diffusivity of feed solution constituents in the active layer.
+%  Nanofiltration membranes have explicit pores on the order of 1 nm in diameter
+%  which are typically tortuous and polydisperse in size. They separate primarily
+%  based on size exclusion as well as Donnan exclusion if the membrane has a
+%  surface charge~\cite{van_der_bruggen_review_2003}.
 
   %MRS14: is selectivity towards water important, or selectivity against what one wants filtered out?
-  The energy consumed during the purification of seawater and wastewater 
-  using RO and NF membranes can be reduced by increasing their selectivity 
-  towards water \cite{werber_materials_2016}. While researchers often focus on
-  improving membrane permeability, the flux of water through a given membrane,
-  it has been shown that increased water permeability only slightly decreases
-  energy requirements \cite{cohen-tanugi_quantifying_2014}.
+%  The energy consumed during the purification of seawater and wastewater 
+%  using RO and NF membranes can be reduced by increasing their selectivity 
+%  towards water \cite{werber_materials_2016}. While researchers often focus on
+%  improving membrane permeability, the flux of water through a given membrane,
+%  it has been shown that increased water permeability only slightly decreases
+%  energy requirements \cite{cohen-tanugi_quantifying_2014}.
 %  since the main energy requirement for a membrane separation is that needed
@@
 %  osmotic pressure of the feed solution\cite{cohen-tanugi_quantifying_2014}. 
-  Often times, multiple membrane passes are required in order to sufficiently
+%  Often times, multiple membrane passes are required in order to sufficiently
   %MRS14: not sure the boric acid part is that relevant, since we don't really talk about 
   %that in the rest of the paper.
-  reduce contaminant levels. For example, boric acid is toxic to humans and 
-  is present in seawater at levels well above acceptable drinking standards.
-  It is difficult to sufficiently separate boric acid in a single pass, meaning
-  multiple passes are needed and energy requirements nearly double \cite{fritzmann_state---art_2007}.
+%  reduce contaminant levels. For example, boric acid is toxic to humans and 
+%  is present in seawater at levels well above acceptable drinking standards.
+%  It is difficult to sufficiently separate boric acid in a single pass, meaning
+%  multiple passes are needed and energy requirements nearly double \cite{fritzmann_state---art_2007}.
 %  This is necessary in the case where high-purity water
@@
 %  when removing boric acid from seawater \cite{fritzmann_state---art_2007}.  
-  The most effective way to reduce energy consumption
-  would be to reduce the number of membrane passes for a given system using 
-  more selective membranes. 
+%  The most effective way to reduce energy consumption
+%  would be to reduce the number of membrane passes for a given system using 
+%  more selective membranes. 
 %   More highly selective membranes have the potential
@@
 
-  Not only will increased selectivity reduce the energy consumption of membrane
-  processes, but it offers a way to recover valuable resources from the feed 
-  streams. Municipal and industrial wastewaters are contaminated by harmful
-  micropollutants, but also contain valuable dissolved solutes. Micropollutants include
-  pharmaceutical and personal care products, hormones, pesticides and industrial
-  chemicals, all of which have adverse effects on human health even at low 
-  concentrations\cite{schwarzenbach_challenge_2006}. A selective membrane has the % There is a need for membranes
-  potential to reject these components while still allowing the passage of valuable 
-  resources for further processing and recovery.
-
-  Municipal wastewaters are rich in carbon, nitrogen and phosphorus-containing 
-  compounds. The recovery of such products, which can be achieved using a 
-  selective membrane, has numerous potential uses \cite{sales_resource_2015}. 
-  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
-  production which will help meet global food demand as population continues
-  to increase \cite{xie_membrane-based_2016}.
+%  Not only will increased selectivity reduce the energy consumption of membrane
+%  processes, but it offers a way to recover valuable resources from the feed 
+%  streams. Municipal and industrial wastewaters are contaminated by harmful
+%  micropollutants, but also contain valuable dissolved solutes. Micropollutants include
+%  pharmaceutical and personal care products, hormones, pesticides and industrial
+%  chemicals, all of which have adverse effects on human health even at low 
+%  concentrations\cite{schwarzenbach_challenge_2006}. A selective membrane has the % There is a need for membranes
+%  potential to reject these components while still allowing the passage of valuable 
+%  resources for further processing and recovery.
+
+%  Municipal wastewaters are rich in carbon, nitrogen and phosphorus-containing 
+%  compounds. The recovery of such products, which can be achieved using a 
+%  selective membrane, has numerous potential uses \cite{sales_resource_2015}. 
+%  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
+%  production which will help meet global food demand as population continues
+%  to increase \cite{xie_membrane-based_2016}.
 
   %MRS14: could possibly be food details, if selective membranes are the key to purifying industrial waste waters. 
-  Industrial waste-waters are often quite complex with up to six times more 
-  total dissolved solids than seawater\cite{werber_materials_2016}. For example, flowback water, produced
-  during hydraulic fracturing of shale formations consists of relatively high
-  concentrations of salts, metals, and soluble organic compounds. The majority
-  of this water is disposed through deep well injection, however there is a growing public concern about
-  its management which has prompted the use of separation technologies such as 
-  RO and NF in order to reduce the volume of contaminated water~\cite{gregory_water_2011}.
-  Some of the dissolved organic compounds in flowback water, such as acetate, 
-  are potentially valuable and can be recovered with highly selective membranes
-  ~\cite{dischinger_application_2017}.
+%  Industrial waste-waters are often quite complex with up to six times more 
+%  total dissolved solids than seawater\cite{werber_materials_2016}. For example, flowback water, produced
+%  during hydraulic fracturing of shale formations consists of relatively high
+%  concentrations of salts, metals, and soluble organic compounds. The majority
+%  of this water is disposed through deep well injection, however there is a growing public concern about
+%  its management which has prompted the use of separation technologies such as 
+%  RO and NF in order to reduce the volume of contaminated water~\cite{gregory_water_2011}.
+%  Some of the dissolved organic compounds in flowback water, such as acetate, 
+%  are potentially valuable and can be recovered with highly selective membranes
+%  ~\cite{dischinger_application_2017}.
 
@@
 
-  Current commercial RO and NF membranes suffer limitations to their selectivity
-  because their structures incorporate some degree of randomness. Although scalable, their 
-  fabrication involves the spontaneous assembly of polymers into disordered structures
-  which offer separation pathways that are tortuous and polydisperse in size 
-  \cite{werber_materials_2016}. Tortuosity increases the effective length that a 
-  solute must travel, while polydispersity limits membrane selectivity.
+%  Current commercial RO and NF membranes suffer limitations to their selectivity
+%  because their structures incorporate some degree of randomness. Although scalable, their 
+%  fabrication involves the spontaneous assembly of polymers into disordered structures
+%  which offer separation pathways that are tortuous and polydisperse in size 
+%  \cite{werber_materials_2016}. Tortuosity increases the effective length that a 
+%  solute must travel, while polydispersity limits membrane selectivity.
 
@@
 
-  Selective separation by a semipermeable membrane barrier is a function of the
-  geometric and chemical interactions of solutes with the membrane material. A
-  molecule's size, shape, charge and polarity combine to determine the degree to
-  which a solute partitions into a membrane and how fast it travels through the
-  membrane. To separate a component from a mixture, one must understand how to
-  design membranes in order to tune the relative transport rates of desired and
-  undesired solutes\cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}.
+%BJC14: probably unnecessary?
+%  Selective separation by a semipermeable membrane barrier is a function of the
+%  geometric and chemical interactions of solutes with the membrane material. A
+%  molecule's size, shape, charge and polarity combine to determine the degree to
+%  which a solute partitions into a membrane and how fast it travels through the
+%  membrane. To separate a component from a mixture, one must understand how to
+%  design membranes in order to tune the relative transport rates of desired and
+%  undesired solutes\cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}.
 
@@
 
-  The feasibility of nanostructured LLC membranes for selective separations has been
-  demonstrated using LLCs that form the type 1 bicontinuous cubic (Q\textsubscript{I})
+  The feasibility of nanostructured LLC membranes for selective separations has
+  been demonstrated using LLCs that form the type 1 bicontinuous cubic
+  (Q\textsubscript{I})
   \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
   and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
-  phases. When 
-  separating organic solutes from NaCl, Q\textsubscript{I} phase membrane filtration
-  experiments have shown selectivity 2--3 times higher than commercial RO and
-  6--12 times higher than commercial NF membranes \cite{dischinger_application_2017}.
-  When separating a series of various sized dyes, the H\textsubscript{II} phase membrane
-  showed complete rejection of dyes bigger than 1.2 nm in size \cite{zhou_supported_2005}.
+  phases. When separating organic solutes from NaCl, Q\textsubscript{I} phase
+  membrane filtration experiments have shown selectivity 2--3 times higher than
+  commercial RO and 6--12 times higher than commercial NF membranes
+  \cite{dischinger_application_2017}. When separating a series of various sized
+  dyes, the H\textsubscript{II} phase membrane showed complete rejection of dyes
+  bigger than 1.2 nm in size \cite{zhou_supported_2005}.
 
@@
 %  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
-  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
-  interconnected pores that prevent optimal through-plane transport. In contrast, the densely packed, 
-  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
-  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
-  However, the hexagonally packed liquid crystalline domains of the H\textsubscript{II} phase generally 
-  form isotropically oriented and therefore mutually unaligned domains which are detrimental to membrane 
-  permeability. This domain scale misalignment has inhibited further development of the this technology, and 
-  research efforts were focused on the Q\textsubscript{I} phase, whose geometry does not require alignment~\cite{dischinger_papers}.
+  Q\textsubscript{I} phase membranes consist of a tortuous network of three
+  dimensionally interconnected pores that prevent optimal through-plane
+  transport. In contrast, the densely packed, non-tortuous and uniform sized
+  pores of H\textsubscript{II} phase membranes represent the ideal geometry for
+  achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.  However, the
+  hexagonally packed liquid crystalline domains of the H\textsubscript{II} phase
+  generally form isotropically oriented and therefore mutually unaligned domains
+  which are detrimental to membrane permeability. This domain scale misalignment
+  has inhibited further development of the this technology, and research efforts
+  were focused on the Q\textsubscript{I} phase, whose geometry does not require
+  alignment~\cite{dischinger_papers}.
 
@@
 
-  However, recently researchers have learned how to macroscopically align the hexagonal
-  domains which has revived research into H\textsubscript{II} phase LLC membranes.
-  In 2014, Feng et al.~showed that one
-  can align Col\textsubscript{h} hexagonal domains, created by the monomer Na-GA3C11,
-  using a magnetic field with subsequent cross-linking to lock the structure in 
-  place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
-  the same result by confining neat monomer between PDMS or glass substrates since 
-  hexagonal mesophases preferentially anchor perpendicular to both surfaces\cite{feng_thin_2016}.
+  However, recently researchers have learned how to macroscopically align the
+  hexagonal domains which has revived research into H\textsubscript{II} phase LLC
+  membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
+  hexagonal domains, created by the monomer Na-GA3C11, using a magnetic field
+  with subsequent cross-linking to lock the structure in
+  place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could
+  obtain the same result by confining neat monomer between PDMS or glass
+  substrates since hexagonal mesophases preferentially anchor perpendicular to
+  both surfaces\cite{feng_thin_2016}.
 %  the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
@@
   Current experimental efforts are focused on extending the method to the
-  H\textsubscript{II} phase and characterizing the performance of these newly aligned systems.
+  H\textsubscript{II} phase and characterizing the performance of these newly
+  aligned systems.
 
@@
 
-  Our current understanding of the molecular details of LLC membranes' nanostructure
-  is not sufficient to be able to precisely design them for specific separations. 
-  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane studies have
-  been limited primarily to Na-GA3C11 with some characterization done after minor 
-  structural modifications. Resel et al.~varied the length of the monomer tails and the
-  counterion used and observed its effect on pore spacing \cite{resel_structural_2000}.
-  In a later study of rejection performance, it was shown that membranes formed by cross-
-  linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes less than 1.2 
-  nm in diameter because the pores are too large \cite{zhou_supported_2005}. We do not
-  yet understand how to controllably reduce the effective pore size or how to tune
-  the chemical environment in the nanopores of this or related materials for
+  Our current understanding of the molecular details of LLC membranes'
+  nanostructure is not sufficient to be able to precisely design them for
+  specific separations. Over the past 20 years, H\textsubscript{II}-phase LLC
+  polymer membrane studies have been limited primarily to Na-GA3C11 with some
+  characterization done after minor structural modifications. Resel et al.~varied
+  the length of the monomer tails and the counterion used and observed its effect
+  on pore spacing \cite{resel_structural_2000}.  In a later study of rejection
+  performance, it was shown that membranes formed by cross- linked Na-GA3C11 in
+  the H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in
+  diameter because the pores are too large \cite{zhou_supported_2005}. We do not
+  yet understand how to controllably reduce the effective pore size or how to
+  tune the chemical environment in the nanopores of this or related materials for
   small molecule separations. The only source of predictive modeling for LLC
   systems have been macroscopic models that likely do not adequately describe
-  transport at these length scales \cite{hatakeyama_water_2011}. Modeling with molecular
-  detail could provide sufficient information about the mechanisms and chemical features
-  to better inform experimental design of similar nanostructured membranes.
+  transport at these length scales \cite{hatakeyama_water_2011}. Modeling with
+  molecular detail could provide sufficient information about the mechanisms and
+  chemical features to better inform experimental design of similar
+  nanostructured membranes.
 

### 2018-08-30 Ben_Manuscripts/structure_paper/Draft.tex
intro rework

@@
   More highly selective nanoporous membranes would be extremely useful in order
-  to perform complex aqeuous separations with seawater and various sources of
-  wastewater. Sodium chloride and boron in seawater, and organic micropollutants
-  found in municipal and industrial wastewaters are a few examples of the
-  diversity of components that make up various water sources. By efficiently
+  to perform complex aqueous separations with seawater and various sources of
+  wastewater. Sodium chloride and boron in seawater \cite{fritzmann_state---art_2007}, and organic micropollutants
+  found in municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are examples of the
+  diverse constituents of various water sources. By efficiently
   separating contaminants from feed solutions with highly selective membranes,
-  one can reduce the number of required membrane passes and post-treatment steps,
-  thus lowering the energy requirements of the separation processes.
+  one can reduce the number of required membrane passes and post-treatment steps
+  needed for a given filtration process \cite{werber_materials_2016}, thus lowering energy requirements.
   Additionally, one can extract valuable resources from the feed streams. For
@@
   formations contains dissolved species such as acetate whose extraction could be
-  economically valuable.
+  economically valuable \cite{dischinger_application_2017}.
 
@@
   commercially dominant membranes lack uniformity which severely impacts their
-  selectivity. Although scalable, their fabrication involves the spontaneous
+  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their fabrication involves the spontaneous
   assembly of polymers into disordered structures which offer separation pathways
@@
 %  \cite{li_desalination_2004}.
-
-  % (4) justify LLCs
-
-  % (5) justify need for simulations
 
@@
 %  \cite{van_der_bruggen_review_2003}.
+
+  % BJC14: (4) justify LLCs
 
@@
 
+  % BJC14: (5) justify need for simulations
+  % BJC14: dishchinger example seems like a good thing to bring up since they 
+  % explicitly state in the paper that they need a better understanding of
+  % transport
   Our current understanding of the molecular details of LLC membranes'
   nanostructure is not sufficient to be able to precisely design them for
-  specific separations. Over the past 20 years, H\textsubscript{II}-phase LLC
+  specific separations. Dischinger et al. attempted to use an empirical model
+  that correlates the physiochemical properties of the counterion used in a 
+  Q\textsubscript{I} phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
+  Although their model showed some qualitative agreement with experiment, the
+  quality of fit of their model was limited due to complex solute-membrane 
+  interactions which could not easily be modeled. Additionally, they observed
+  an unexpected discrepancy in the relationship between uncharged solute
+  rejection and water permeability which will require a more in-depth knowledge of
+  the difference between solute and solvent transport.
+
+  Over the past 20 years, H\textsubscript{II}-phase LLC
   polymer membrane studies have been limited primarily to Na-GA3C11 with some
@@
   on pore spacing \cite{resel_structural_2000}.  In a later study of rejection
-  performance, it was shown that membranes formed by cross- linked Na-GA3C11 in
+  performance, it was shown that membranes formed by cross-linked Na-GA3C11 in
   the H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in

### 2018-08-30 Ben_Manuscripts/structure_paper/Draft.tex
intro edits

@@
   to perform complex aqueous separations with seawater and various sources of
-  wastewater. Sodium chloride and boron in seawater \cite{fritzmann_state---art_2007}, and organic micropollutants
-  found in municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are examples of the
-  diverse constituents of various water sources. By efficiently
+  wastewater. Sodium chloride and boron in seawater
+  \cite{fritzmann_state---art_2007}, and organic micropollutants found in
+  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are
+  examples of the diverse constituents of these water sources. By efficiently
   separating contaminants from feed solutions with highly selective membranes,
   one can reduce the number of required membrane passes and post-treatment steps
-  needed for a given filtration process \cite{werber_materials_2016}, thus lowering energy requirements.
-  Additionally, one can extract valuable resources from the feed streams. For
-  example, flowback water produced during hydraulic fracturing of shale
-  formations contains dissolved species such as acetate whose extraction could be
-  economically valuable \cite{dischinger_application_2017}.
+  needed for a given filtration process \cite{werber_materials_2016}, thus
+  lowering energy requirements. Additionally, one can extract valuable resources
+  from the feed streams. For example, flowback water produced during hydraulic
+  fracturing of shale formations contains dissolved species such as acetate whose
+  extraction has economic value \cite{dischinger_application_2017}.
 
@@
 
- % (2) existing nanoporous membranes + drawbacks
+ % BJC14: (2) existing nanoporous membranes + drawbacks
 
@@
   commercially dominant membranes lack uniformity which severely impacts their
-  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their fabrication involves the spontaneous
-  assembly of polymers into disordered structures which offer separation pathways
-  that are tortuous and polydisperse in size \cite{werber_materials_2016}.
-  Tortuosity increases the effective length that a solute must travel, while
-  polydispersity limits membrane selectivity.
-
-  % (3) justification for why nanostructured membranes are a good idea for this
+  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
+  fabrication involves the spontaneous assembly of polymers into disordered
+  structures which offer separation pathways that are tortuous and polydisperse
+  in size \cite{werber_materials_2016}. Tortuosity increases the effective
+  length that a solute must travel, while polydispersity limits membrane
+  selectivity.
+
+  % BJC14: (3) justification for why nanostructured membranes are a good idea for this
   % long-term route towards highly selective membranes are those that are nanostructured
@@
   Preliminary evidence has shown that crosslinked lyotropic liquid crystal
-  (LLC) membranes may be capable of performing highly selective separations. LLCs
-  are amphiphilic molecules that have the ability to self-assemble into porous
-  nanostructures \cite{smith_ordered_1997} and can be crosslinked to create
-  mechanically strong membrane films with pores on the order of 1 nm in diameter
-  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane
-  pores are uniform in size because they are self-assembled. Since LLC membranes
-  lack a pore size distribution, they inherently exhibit high selectivity due to
-  their strict molecular weight cut-off (MWCO)~\cite{zhou_supported_2005}.
-  Additionally, the LLC monomers examined in this paper are salts, and therefore
-  lead to Donnan exclusion of ions in solution. The membrane gains a net surface
-  charge when counterions from the head groups that line the pore walls escape
-  into the feed solution in an effort to balance the gradients of concentration
-  and electric potential \cite{donnan_theory_1995}.
+  (LLC) membranes are scalable and may be capable of performing highly selective
+  separations. LLCs are amphiphilic molecules that have the ability to
+  self-assemble into porous nanostructures \cite{smith_ordered_1997} and can be
+  crosslinked to create mechanically strong membrane films with pores on the
+  order of 1 nm in diameter \cite{zhou_supported_2005}. Unlike most commercial NF
+  membranes, LLC membrane pores are uniform in size because they are
+  self-assembled. Since LLC membranes lack a pore size distribution, they
+  inherently exhibit high selectivity due to their strict molecular weight
+  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
+  examined in this paper are salts, and therefore lead to Donnan exclusion of
+  ions in solution. The membrane gains a net surface charge when counterions from
+  the head groups that line the pore walls escape into the feed solution in an
+  effort to balance the gradients of concentration and electric potential
+  \cite{donnan_theory_1995}.
 
@@
   which are detrimental to membrane permeability. This domain scale misalignment
-  has inhibited further development of the this technology, and research efforts
+  have inhibited further development of the this technology, and research efforts
   were focused on the Q\textsubscript{I} phase, whose geometry does not require
@@
   nanostructured membranes.
+
+  %BJC14: nothing new after this point
 

### 2018-08-31 Ben_Manuscripts/structure_paper/Draft.tex
some comments.

@@
 
-%MRS5: could be punchier. I will keep thinking.  I should be the last author.  Chen the names that Joe and Matt wanttu use (presumably with some middle initial?
+%MRS5: could be punchier. I will keep thinking.  
 \title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
@@
   separating contaminants from feed solutions with highly selective membranes,
-  one can reduce the number of required membrane passes and post-treatment steps
+  it is is possibl to reduce the number of required membrane passes and post-treatment steps
   needed for a given filtration process \cite{werber_materials_2016}, thus
@@
   filtration processes that can be used to separate solutes on the order of 1 nm
-  in size and smaller, as well as ions, however the porous architecture of
-  commercially dominant membranes lack uniformity which severely impacts their
+  in size and smaller, as well as ions. However the porous architecture of
+  commercially 
+  %MRS15: may be too strong an assertion.
+  %dominant
+  available 
+  membranes lack uniformity which severely impacts their
   selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
@@
   % long-term route towards highly selective membranes are those that are nanostructured
-  Nanostructured porous membrane materials have become increasingly popular for
+  %MRS15: popilar for separations applications would imply the are getting a larger market share now, 
+  %though my impression is that they are research topics of heavy interest, but not yet that commercially viable.  Check my chainge below.
+  Nanostructured porous membrane materials have become 
+  %increasingly popular
+  an increasingly popular research area for
   aqueous separations applications because they offer the ability to control pore
   architecture at the molecular scale, thereby permitting the design of
-  solute-specific separation membranes \cite{humplik_nanostructured_2011},
-  however their development has been limited by the ability to synthesize and
-  scale various fundamentally sound technologies. Graphene sheets are atomically
+  solute-specific separation membranes \cite{humplik_nanostructured_2011}.
+  However their development has been limited by the ability to synthesize and
+  scale 
+  %MRS15: not sure what you mean by ``fundamentally sound technologies''.
+THat the underlying principles are good, but that scaling is hard?
+Fundamentally sound seems to suggest that both principles and scaling are good, but that's not what the implication is.
+  various fundamentally sound technologies. Graphene sheets are atomically
   thick which results in excellent water permeability but defects during

### 2018-09-11 Ben_Manuscripts/structure_paper/Draft.tex
new analysis of disorder in quenched systems

--- 2018-08-30 Ben_Manuscripts/structure_paper/Draft.tex
@@
 
-  We parameterized the liquid crystal monomer Na-GA3C11 using the Generalized AMBER
-  Force Field (GAFF) \cite{wang_development_2004} with the Antechamber package
-  \cite{wang_automatic_2006} provided with AmberTools16
-  \cite{case_ambertools16_2016}. We assigned atomic charges using the am1bccsym
-  method of \texttt{molcharge} shipped with QUACPAC from Openeye Scientific
-  Software. We ran all molecular dynamics simulations using GROMACS 2016
-  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
+  We parameterized the interaction potential for the liquid crystal monomer 
+  Na-GA3C11 using the Generalized AMBER Force Field (GAFF) 
+  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006} 
+  provided with AmberTools16 \cite{case_ambertools16_2016}. We assigned atomic
+  charges using the am1bccsym method of \texttt{molcharge} shipped with QUACPAC
+  from Openeye Scientific Software. We ran all molecular dynamics simulations 
+  using GROMACS 2016 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
 
@@
   Supporting Information). 
+  % BJC15: added to address Matt's concern
+  The pore spacings calculated in this way are consistent
+  with one half of the $x$ and $y$ box vectors (See, Table S-\ref{S-table:p2p}). However
+  our method for their calculation does a better job capturing the spread of 
+  pore-to-pore distances.
 
@@
   distance between monomer head groups is too large, likely due to failures
-  of the forcefield to appropriately model $\pi-\pi$ interactions. The intensity
+  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
   of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
@@
 
-  The architecture of each column is therefore likely in between sandwiched and parallel
-  displaced. The parallel displaced configuration that we have simulated in this
+  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
+  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
+  % “in between sandwiched and parallel displaced” looks like would be helpful"
+  The architecture of each column is therefore likely in between our sandwiched and parallel
+  displaced configurations. The parallel displaced configuration that we have simulated in this
   paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
@@
 
-  Because disorder among head groups in the simulated atomistic systems is largely
-  determined by each system's quenched configuration, one would need to average an
-  ensemble of simulations in order to optimally match the experimental WAXS pattern. 
-  Both the initial configuration and initial velocity randomization lead to 
-  different quenched configurations every time we run an equilibration simulation.
-  Although the simulated XRD pattern changes dynamically as we simulate the system
-  due to thermal fluctuations, its features are largely determined by the initial 
-  quenched configuration. Here we assume that the timescales for large scale 
-  rearrangements of the system are much longer than what we can feasibly simulate. 
-  %MRS12: I don't think this is necessary.  They should reproduce the same findings, if they use a similar quenched configuration. 
-  %As a result, it will be difficult to exactly reproduce the work here, but we are
-  %confident that one can draw the same conclusions using our methodology.
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{pd_36.eps}
+  \caption{}\label{fig:pd_36}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{pd_lt36.eps}
+  \caption{}\label{fig:pd_lt36}
+  \end{subfigure}
+  \caption{Head groups are likely stack in a configuration between sandwiched and
+  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
+  per columns, we placed head groups so the angle, $\theta$, between vectors extending
+  from vertically stacked head groups to the pore center equals 36$\degree$ 
+  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
+  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
+  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
+  configuration.}\label{fig:between_pd}
+  \end{figure}
+
+% BJC15: this paragraph reframed and expanded below
+%  Because disorder among head groups in the simulated 
+%  atomistic systems is largely determined by each system's quenched configuration,
+%  one would need to average an ensemble of simulations in order to optimally match the experimental WAXS pattern. 
+%  Both the initial configuration and initial velocity randomization lead to 
+%  different quenched configurations every time we run an equilibration simulation.
+%  Although the simulated XRD pattern changes dynamically as we simulate the system
+%  due to thermal fluctuations, its features are largely determined by the initial 
+%  quenched configuration. Here we assume that the timescales for large scale 
+%  rearrangements of the system are much longer than what we can feasibly simulate.
+
+  Since the dynamics of this system appear to be quite slow, we can learn more about
+  their time-averaged structure by studying ensembles of simulations.
+  Disorder among head groups in the simulated atomistic systems is largely determined
+  by each system's quenched configuration. We observe rapid reorganization of our 
+  initial configurations into configurations with quenched disorder that does not
+  vary significantly for the remainder of the % BJC15: I could quantify this more and put in supporting info
+  simulation time. For that reason, we created ensembles of 40 simulations in both
+  the parallel displaced and sandwiched configurations. We used the same equilibration
+  technique as above (see section~\ref{section:equilibration}), however we stopped 
+  the equilibration after 5 ns of unrestrained simulation. We simulated XRD patterns
+  from the 40 concatenated trajectories. The $q_r$ cross-sections generated from the 
+  two concatenated trajectories are shown in Figure~\ref{fig:ensemble_XRD}. 
+  Qualitatively, the $q_r$ cross-sections of R-$\pi$ are nearly smooth, with small
+  spikes near $q_r$=0. The data suggests that the average
+  intensity of R-$\pi$ in sandwiched systems is about 3$\times$ higher than that in the
+  parallel displaced configuration. Overall, the intensity of R-$\pi$ generated from the
+  parallel displaced ensemble shows the best agreement with experiment so far. For
+  simplicity, we will limit the following discussion to the parallel displaced 
+  configuration. Equivalent data is available for the sandwiched configuration in the
+  supporting information.
+  %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
+  % However, I can switch it sandwiched very easily.
+
+  %BJC15: This figure might not be necessary. Do the comparisons of emperical
+  % cumulative distribution functions make the same point? 
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.png}
+  \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{offset_ensemble_rsection.png}
+  \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
+  \end{subfigure}
+  \caption{The $q_r$ section of R-$\pi$ is much smoother when simulated XRD patterns
+  		   are generated from an ensemble of 40 independent simulations. The maximum 
+  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
+  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
+  \end{figure}
+
+  Independent simulations exhibit similar amounts of quenched disorder. For 
+  each, we measured the deviation of the head group centers of mass from their
+  idealized positions (see section~\ref{method:simple_systems}). 
+  We created histograms of the standard deviations of each distribution which
+  are shown in Figure~\ref{fig:ensemble_stds}. The distributions of standard deviations
+  are fairly tight with ($\sigma_\sigma_z$, $\sigma_\sigma_r$, $\sigma_\sigma_\theta$) = (0.011 nm, 
+  0.007 nm , 0.022 radians). We pooled the deviations from idealized positions 
+  from all independent simulations in order to create the distributions shown in 
+  Figure~\ref{fig:offset_ensemble_pooled}. The distributions appear 
+  symmetric meaning that there is an equal chance for a head group to displace
+  in the positive or negative $z$, $r$ or $\theta$-direction. We verified that
+  this is the case for individual center of masses. 
+  % For a given system, there are 400 head groups. 
+  If we consider the center of mass of the first head group, we expect that the
+  distribution of its deviation from its idealized position among all the 
+  independent simulations
+%  the $z$, $r$, and $\theta$ directions 
+  should be symmetric about its idealized position. We can calculate the 
+  empirical cumulative distribution function (ECDF) 
+  of this distribution of deviations. 
+  % Each ECDF contains 40 data points, one from each independent simulation.
+  The ECDFs of 5 randomly selected centers of 
+  mass are shown in Figure~\ref{fig:offset_ecdfs} (colored lines). We also calculated 
+  the ECDF from the full distributions in Figure~\ref{fig:offset_ensemble_pooled}
+  (black line with error bars). We generated error bars that represent the 95\% 
+  confidence intervals, by randomly sampling 40 values (the same as the number 
+  of independent simulations) from the distributions in 
+  Figure~\ref{fig:offset_ensemble_pooled}, then measuring the deviation between
+  the sampled ECDF and the full ECDF. The center of mass ECDFs lie between the
+  error bars of the full ECDF within reason. This provides further evidence that
+  each center of mass moves independently, in random directions when systems
+  quench.
+
+% Sandwiched: (0.019 nm, 0.007 nm, 0.023 radians)
+
+  \begin{figure}[!htb]
+  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.png}
+%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_stds.png}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=0.45\textwidth]{offset_ensemble_stds.png}
+%  \caption{Parallel Displaced}\label{fig:offset_ensemble_stds.png}
+%  \end{subfigure}
+  \caption{There is a narrow spread in the standard deviation of
+  quenched disorder for each independent configuration.}\label{fig:ensemble_stds}
+  \end{figure}
+
+  %BJC15: will not waste much time formatting until we converge on a figure 
+  \begin{figure}[!htb]
+  \centering
+%  \begin{subfigure}{\textwidth}
+%  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.png}
+%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_pooled.png}
+%  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{offset_ensemble_pooled.png}
+  \caption{Distributions of deviations from ideal positions generated with data
+  from all independent simulations}\label{fig:offset_ensemble_pooled}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{offset_ecdfs.png}
+  \caption{Emperical cumulative distribution functions generated from (a) and
+  from simulation ensembles.}\label{fig:offset_ecdfs}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
+  \caption{Radial density of select monomer components.}\label{fig:offset_ensemble_regional_density}
+  \end{subfigure}
+  \caption{The distributions of the deviations of head group center of masses
+  from their idealized positions generated using pooled data from all
+  frames of each independent configuration is symmetric. This implies that 
+  there is equal probability for a head group to displace in the positive
+  or negative $z$, $r$ or $\theta$-direction.}\label{fig:full_ensemble_distributions}
+  \end{figure}
 
@@
   the ordered basin with 1 wt\% water since we believe its structure is the 
-  closest match to experiment. Our model estimates the ionic conductivity within
-  one order of magnitude of experiment (Figure~\ref{fig:ionic_conductivity}). We
-  verified the value calculated by the Nernst-Einstein relationship using 
-  the collective diffusion model\cite{liu_collective_2013} 
+  closest match to experiment. Our model estimates the ionic conductivity to be
+  $(5.92 \pm 0.05)\times$\num{e-5}~S/m, about 5 times higher than the experimental value of 
+  $(1.3 \pm 0.1)\times$\num{e-5}~S/m. We verified the value calculated by the Nernst-Einstein
+  relationship using the collective diffusion model\cite{liu_collective_2013} 
   (See section S~\ref{S-fig:conductivity}). The values calculated by the 
@@
 
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{IC_nernst.png}
-  \caption{The calculated ionic conductivity of the simulated system is approximately
-  one order of magnitude higher than experiment.}\label{fig:ionic_conductivity}
-  \end{figure}
+% BJC15: removed figure
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{IC_nernst.png}
+%  \caption{The calculated ionic conductivity of the simulated system is approximately
+%  one order of magnitude higher than experiment.}\label{fig:ionic_conductivity}
+%  \end{figure}
 
@@
   configurations contain a high level of dependence between monomer columns.
-  Finally, we observed that our model can only produce R-double when we add small amounts of
-  % I removed the specific details, since it implied that 2% wouldn't do it, which we don't know.
-  %1 wt\% 
-water to the system. This observation has possible implications for the
-  reproducibility of the experimental results from Feng et al. since they claim
-  that their membrane is completely dry.
+  Finally, we observed that our model can only produce R-double when we add 
+  small amounts of water to the system. This observation has possible implications
+  for the reproducibility of the experimental results from Feng et al. since they
+  claim that their membrane is completely dry.
 
@@
 %  that is in good agreement with experimental data.
+
+  % BJC15: first pass at a brief future work paragraph
+  Future work, based on what has been learned in this study, may help further improve the 
+  structural agreement between experiment and simulation. We may be able to 
+  modify the GAFF force field or use a different force field in order to better
+  capture the $\pi-\pi$ interactions which draw stacked monomers closer together. 
+  We can study ensembles of long simulations in order to observe more averaged 
+  structure and to create more experimentally consistent XRD patterns. Finally, we can
+  run extremely long simulations (on the order of \SI{}{\micro s}) in order to better 
+  quantify the time scales for large scale rearrangements to occur.
 

### 2018-09-11 Ben_Manuscripts/structure_paper/supporting_information.tex
new analysis of disorder in quenched systems

@@
 
-%  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
-% 
-% %BJC: is it really necessary to explain this if I release the code? I don't explain
-% %any of the other stats I calculate. 
-%  We are interested in 5 pore-to-pore distances which should all be
-%  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
-%  the 5 distances are independent. We can calculate a trajectory of spacing
-%  versus time for each of the 5 distances. We calculated the average pore-to-pore
-%  spacing and its uncertainty according to the following procedure:
-%   \begin{enumerate}
-%	\item We calculated the time when each of the pore-to-pore distances
-%	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
-%	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
-%	after the largest of the five values.
-%	\item We calculated how long it takes for the data in each of the 5
-%	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
-%	\cite{chodera_simple_2016,shirts_statistically_2008}. 
-%	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
-%	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
-%	five sub-trajectories of pore-to-pore spacings.   
-%	\item We generate statistics using the bootstrapping technique. For
-%	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
-%	sampling from the trajectory blocks. 
-%	\item The average pore-to-pore distance is the mean of all pore
-%	spacings among all bootstrap trials.
-%	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
-%	pore spacing for each pore over all bootstrap trials. Using the 5 average 
-%	pore-to-pore distances, we calculate the spread with:
-%	\begin{equation}
-%	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
-%	\label{equation:p2p_stats}
-%	\end{equation}
-%	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
-%	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
-%	spacings.
-%	
-%  \end{enumerate}
-%  \begin{figure}[!htb]
-%	\centering
-%	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
-%	\caption{There are five pore-to-pore distances that are equal in a perfect
-%		hexagon. If each number in the diagram represents the center of a
-%		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
-%		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
-%		are independent. For example, the distance from 1 to 4 is defined by
-%		the location of all other pore centers.}
-%	\label{fig:p2p_diagram}
-%  \end{figure}
+  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
+
+ %BJC: is it really necessary to explain this if I release the code? I don't explain
+ %any of the other stats I calculate. 
+  We are interested in 5 pore-to-pore distances which should all be
+  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
+  the 5 distances are independent. We can calculate a trajectory of spacing
+  versus time for each of the 5 distances. We calculated the average pore-to-pore
+  spacing and its uncertainty according to the following procedure:
+   \begin{enumerate}
+	\item We calculated the time when each of the pore-to-pore distances
+	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
+	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
+	after the largest of the five values.
+	\item We calculated how long it takes for the data in each of the 5
+	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
+	\cite{chodera_simple_2016,shirts_statistically_2008}. 
+	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
+	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
+	five sub-trajectories of pore-to-pore spacings.   
+	\item We generate statistics using the bootstrapping technique. For
+	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
+	sampling from the trajectory blocks. 
+	\item The average pore-to-pore distance is the mean of all pore
+	spacings among all bootstrap trials.
+	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
+	pore spacing for each pore over all bootstrap trials. Using the 5 average 
+	pore-to-pore distances, we calculate the spread with:
+	\begin{equation}
+	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
+	\label{equation:p2p_stats}
+	\end{equation}
+	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
+	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
+	spacings.
+
+  \end{enumerate}
+  \begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
+	\caption{There are five pore-to-pore distances that are equal in a perfect
+		hexagon. If each number in the diagram represents the center of a
+		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
+		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
+		are independent. For example, the distance from 1 to 4 is defined by
+		the location of all other pore centers.}
+	\label{fig:p2p_diagram}
+  \end{figure}
+
+  Alternatively, one can calculate the pore spacing as half of the $x$ and $y$
+  box vectors, however this technique does not fully capture the uncertainty
+  in the pore-to-pore distances.
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cc}
+  \toprule
+  System                         & Pore Spacing ($nm$) & Pore Spacing ($nm$)              \\
+                                 & Pore centers        & $\dfrac{x-box vector}{2}$ ($nm$) \\ 
+  \midrule
+  Sandwiched, Ordered            & 4.18 $\pm$ 0.13     & 4.16 $\pm$ 0.01                  \\
+  Parallel Displaced, Ordered    & 4.17 $\pm$ 0.12     & 4.18 $\pm$ 0.01                  \\
+  Sandwiched, Disordered         & 4.05 $\pm$ 0.14     & 4.01 $\pm$ 0.01                  \\
+  Parallel Displaced, Disordered & 4.03 $\pm$ 0.07     & 4.01 $\pm$ 0.01                  \\
+  \bottomrule
+  \end{tabular}
+  \caption{The pore spacing measured in two ways agree within uncertainty. In the main
+  text, we report values calculated by measuring the average distance between pore centers. 
+  Alternatively, one can estimate the pore spacing as half of the $x$ and $y$ box vectors.
+  Both methods agree within uncertainty, but measuring the distance between pore centers
+  does a better job of showing the spread of pore-to-pore distances.}~\label{table:p2p}
+  \end{table}
 

### 2018-09-11 analysis/Structure_char.py

@@ -140,7 +140,7 @@ def avg_pore_loc(npores, pos, buffer):
 
         for j in range(npores):
             for k in range(comp_ppore*j, comp_ppore*(j + 1)):
-                p_center[:, j] += pos[:2, k]
+                p_center[:, j] += pos[k, :2]
             p_center[:, j] /= comp_ppore
 
     else:

### 2018-09-11 setup/equil.sh

@@ -38,7 +38,7 @@ else
     GMX="gmx"
 fi
 
-${python} ${DIR}/build2.py -pd 0.35
+${python} ${DIR}/build2.py --no_column_shift #-pd 0.35
 
 # make input files
 ${python} ${DIR}/input.py -b ${BUILD_MON} -l 50 --restraints ${restraint_residue} --temp ${T} -f 50 --genvel yes -c ${start_config} -s 50000
@@ -81,8 +81,8 @@ done
 ${python} ${DIR}/input.py -b ${BUILD_MON} -l 5000 --temp ${T} -f 50 --genvel no -c ${start_config} --barostat berendsen
 
 gmx grompp -f npt.mdp -p topol.top -c npt.gro -o berendsen
-exit
 ${GMX} mdrun -v -deffnm berendsen
-${python} ${DIR}/input.py -b ${BUILD_MON} -l ${equil_length} --temp ${T} -f 10000 --barostat Parrinello-Rahman --genvel no -c berendsen.gro
+
+#${python} ${DIR}/input.py -b ${BUILD_MON} -l ${equil_length} --temp ${T} -f 10000 --barostat Parrinello-Rahman --genvel no -c berendsen.gro
 gmx grompp -f npt.mdp -p topol.top -c berendsen.gro -o PR
 ${GMX} mdrun -v -deffnm PR

### 2018-09-11 Ben_Manuscripts/structure_paper/Draft.tex
Merge branch 'master' of github.com:shirtsgroup/LLC_Membranes

@@
   to perform complex aqueous separations with seawater and various sources of
-  wastewater. Sodium chloride and boron in seawater \cite{fritzmann_state---art_2007}, and organic micropollutants
-  found in municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are examples of the
-  diverse constituents of various water sources. By efficiently
+  wastewater. Sodium chloride and boron in seawater
+  \cite{fritzmann_state---art_2007}, and organic micropollutants found in
+  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are
+  examples of the diverse constituents of these water sources. By efficiently
   separating contaminants from feed solutions with highly selective membranes,
-  one can reduce the number of required membrane passes and post-treatment steps
-  needed for a given filtration process \cite{werber_materials_2016}, thus lowering energy requirements.
-  Additionally, one can extract valuable resources from the feed streams. For
-  example, flowback water produced during hydraulic fracturing of shale
-  formations contains dissolved species such as acetate whose extraction could be
-  economically valuable \cite{dischinger_application_2017}.
+  it is is possibl to reduce the number of required membrane passes and post-treatment steps
+  needed for a given filtration process \cite{werber_materials_2016}, thus
+  lowering energy requirements. Additionally, one can extract valuable resources
+  from the feed streams. For example, flowback water produced during hydraulic
+  fracturing of shale formations contains dissolved species such as acetate whose
+  extraction has economic value \cite{dischinger_application_2017}.
 
@@
   filtration processes that can be used to separate solutes on the order of 1 nm
-  in size and smaller, as well as ions, however the porous architecture of
-  commercially dominant membranes lack uniformity which severely impacts their
-  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their fabrication involves the spontaneous
-  assembly of polymers into disordered structures which offer separation pathways
-  that are tortuous and polydisperse in size \cite{werber_materials_2016}.
-  Tortuosity increases the effective length that a solute must travel, while
-  polydispersity limits membrane selectivity.
-
-  % (3) justification for why nanostructured membranes are a good idea for this
+  in size and smaller, as well as ions. However the porous architecture of
+  commercially 
+  %MRS15: may be too strong an assertion.
+  %dominant
+  available 
+  membranes lack uniformity which severely impacts their
+  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
+  fabrication involves the spontaneous assembly of polymers into disordered
+  structures which offer separation pathways that are tortuous and polydisperse
+  in size \cite{werber_materials_2016}. Tortuosity increases the effective
+  length that a solute must travel, while polydispersity limits membrane
+  selectivity.
+
+  % BJC14: (3) justification for why nanostructured membranes are a good idea for this
   % long-term route towards highly selective membranes are those that are nanostructured
-  Nanostructured porous membrane materials have become increasingly popular for
+  %MRS15: popilar for separations applications would imply the are getting a larger market share now, 
+  %though my impression is that they are research topics of heavy interest, but not yet that commercially viable.  Check my chainge below.
+  Nanostructured porous membrane materials have become 
+  %increasingly popular
+  an increasingly popular research area for
   aqueous separations applications because they offer the ability to control pore
   architecture at the molecular scale, thereby permitting the design of
-  solute-specific separation membranes \cite{humplik_nanostructured_2011},
-  however their development has been limited by the ability to synthesize and
-  scale various fundamentally sound technologies. Graphene sheets are atomically
+  solute-specific separation membranes \cite{humplik_nanostructured_2011}.
+  However their development has been limited by the ability to synthesize and
+  scale 
+  %MRS15: not sure what you mean by ``fundamentally sound technologies''.
+THat the underlying principles are good, but that scaling is hard?
+Fundamentally sound seems to suggest that both principles and scaling are good, but that's not what the implication is.
+  various fundamentally sound technologies. Graphene sheets are atomically
   thick which results in excellent water permeability but defects during

### 2018-09-12 Ben_Manuscripts/structure_paper/Draft.tex
Addition of quenched disorder discussion to draft with attempted minimization of flow disruption

@@
 
+  \subsubsection{\textit{Radial distribution functions}}
+
+  We explored the pores' compositions by measuring the average number densities
+  of various monomer components as a function of distance from the pore centers.
+  We looked at the average number density of sodium ions, aromatic rings and 
+  carbon atoms making up the monomer tails. We binned the radial distance of all
+  atoms in each group from the pore centers, then normalized by the volume of the
+  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}).
+
   \subsection{Simplified Systems}\label{method:simple_systems}
@@
 
-  \subsubsection{\textit{Radial distribution functions}}
-
-  We explored the pores' compositions by measuring the average number densities
-  of various monomer components as a function of distance from the pore centers.
-  We looked at the average number density of sodium ions, aromatic rings and 
-  carbon atoms making up the monomer tails. We binned the radial distance of all
-  atoms in each group from the pore centers, then normalized by the volume of the
-  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}).
-
-  \subsubsection{\textit{Ionic conductivity calculations}}
+  \subsection{\textit{Ionic conductivity calculations}}
 
@@
   system at 500 K then annealed it to 300 K in an attempt to coerce the tails into
-  a more tightly packed configuration, however we saw no improvement in packing
+  a more tightly packed configuration, but we saw no improvement in packing
   distance over our 300 K models. See section S-TBD for details.
@@
 	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
-	  $theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
+	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
 	  we double the disorder (Noise factor = 2), the FWHM decreases by
 	  51\%.}\label{fig:qy_fwhm}
-  \end{figure}
-
-  We can explain the discrepancies between R-$\pi$ seen experimentally
-  and in simulation using what we have shown in this section. The stacking
-  distance between monomer head groups is too large, likely due to failures
-  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
-  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
-  ordering in the $z$-direction in addition to high degrees of correlation 
-  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
-  which is also likely a consequence of columns that are too highly correlated.
-
-  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
-  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
-  % “in between sandwiched and parallel displaced” looks like would be helpful"
-  The architecture of each column is therefore likely in between our sandwiched and parallel
-  displaced configurations. The parallel displaced configuration that we have simulated in this
-  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
-  stacking mode. The experimental WAXS pattern shows faint off-axis features at the
-  same $q_r$ value as R-double which is only present in simulated patterns generated from
-  parallel displaced configurations. The monomers may prefer to be parallel displaced, but
-  their displacement is likely only slightly shifted, on the $xy$ plane, from the
-  center of mass of their vertically adjacent neighbors. In this way, columns can
-  more easily act independently while maintaining a parallel displaced structure.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{pd_36.eps}
-  \caption{}\label{fig:pd_36}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{pd_lt36.eps}
-  \caption{}\label{fig:pd_lt36}
-  \end{subfigure}
-  \caption{Head groups are likely stack in a configuration between sandwiched and
-  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
-  per columns, we placed head groups so the angle, $\theta$, between vectors extending
-  from vertically stacked head groups to the pore center equals 36$\degree$ 
-  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
-  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
-  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
-  configuration.}\label{fig:between_pd}
   \end{figure}
@@
 
-  Since the dynamics of this system appear to be quite slow, we can learn more about
-  their time-averaged structure by studying ensembles of simulations.
-  Disorder among head groups in the simulated atomistic systems is largely determined
-  by each system's quenched configuration. We observe rapid reorganization of our 
-  initial configurations into configurations with quenched disorder that does not
-  vary significantly for the remainder of the % BJC15: I could quantify this more and put in supporting info
-  simulation time. For that reason, we created ensembles of 40 simulations in both
-  the parallel displaced and sandwiched configurations. We used the same equilibration
-  technique as above (see section~\ref{section:equilibration}), however we stopped 
-  the equilibration after 5 ns of unrestrained simulation. We simulated XRD patterns
-  from the 40 concatenated trajectories. The $q_r$ cross-sections generated from the 
-  two concatenated trajectories are shown in Figure~\ref{fig:ensemble_XRD}. 
-  Qualitatively, the $q_r$ cross-sections of R-$\pi$ are nearly smooth, with small
-  spikes near $q_r$=0. The data suggests that the average
-  intensity of R-$\pi$ in sandwiched systems is about 3$\times$ higher than that in the
-  parallel displaced configuration. Overall, the intensity of R-$\pi$ generated from the
-  parallel displaced ensemble shows the best agreement with experiment so far. For
-  simplicity, we will limit the following discussion to the parallel displaced 
-  configuration. Equivalent data is available for the sandwiched configuration in the
-  supporting information.
+  Since the dynamics of this system appear to be quite slow, and consequently most of
+  our analysis has been focused on a small set of quenched configurations whose 
+  structures do not vary significantly with time, we attempted
+  to learn more about their time-averaged structures by studying ensembles of simulations.
+%  Disorder among head groups in the simulated atomistic systems is largely determined
+%  by each system's quenched configuration. We observe rapid reorganization of our 
+%  initial configurations into configurations with quenched disorder that does not
+%  vary significantly for the remainder of the
+%  simulation time. For that reason, 
+  We created ensembles of 40 simulations in both the parallel displaced and 
+  sandwiched configurations. We used the same equilibration technique as above 
+  (see section~\ref{section:equilibration}), however we built the initial
+  configurations with randomly displaced columns in the $z$-direction and
+  then stopped their equilibration after 5 ns of unrestrained simulation. We 
+  simulated XRD patterns from the 40 concatenated trajectories. The $q_r$ 
+  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
+  in Figure~\ref{fig:ensemble_XRD}. Qualitatively, the cross-sections
+  of are nearly smooth, with small spikes near $q_r$=0. The data 
+  suggests that the average intensity of R-$\pi$ in sandwiched systems is 
+  about 3$\times$ higher than that in the parallel displaced configuration. 
+  Overall, the intensity of R-$\pi$ generated from the parallel displaced 
+  ensemble shows the best agreement with experiment so far. For simplicity, 
+  we will limit the following discussion to the parallel displaced configuration.
+  Equivalent data is available for the sandwiched configuration in the
+  supporting information. %BJC15: to be added
   %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
-  % However, I can switch it sandwiched very easily.
-
-  %BJC15: This figure might not be necessary. Do the comparisons of emperical
-  % cumulative distribution functions make the same point? 
+  % However, I can switch it to sandwiched very easily. The discussion below will remain the same
+
   \begin{figure}[!htb]
@@
   \end{subfigure}
-  \caption{The $q_r$ section of R-$\pi$ is much smoother when simulated XRD patterns
-  		   are generated from an ensemble of 40 independent simulations. The maximum 
+  \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
+  		   patterns from an ensemble of 40 independent simulations. The maximum 
   		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
@@
 
-  Independent simulations exhibit similar amounts of quenched disorder. For 
-  each, we measured the deviation of the head group centers of mass from their
-  idealized positions (see section~\ref{method:simple_systems}). 
-  We created histograms of the standard deviations of each distribution which
-  are shown in Figure~\ref{fig:ensemble_stds}. The distributions of standard deviations
-  are fairly tight with ($\sigma_\sigma_z$, $\sigma_\sigma_r$, $\sigma_\sigma_\theta$) = (0.011 nm, 
-  0.007 nm , 0.022 radians). We pooled the deviations from idealized positions 
+  Independent simulations exhibit similar amounts of quenched disorder. 
+  We pooled the deviations of each head group COM from idealized positions
   from all independent simulations in order to create the distributions shown in 
-  Figure~\ref{fig:offset_ensemble_pooled}. The distributions appear 
+  Figure~\ref{fig:offset_ensemble_pooled} 
+  (see section~\ref{method:simple_systems}). The distributions appear 
   symmetric meaning that there is an equal chance for a head group to displace
   in the positive or negative $z$, $r$ or $\theta$-direction. We verified that
-  this is the case for individual center of masses. 
+  this is the case for individual COMs. 
   % For a given system, there are 400 head groups. 
-  If we consider the center of mass of the first head group, we expect that the
-  distribution of its deviation from its idealized position among all the 
+  If we consider the COM of a given head group, we expect that the
+  distribution of its deviations from its idealized position among all the 
   independent simulations
@@
   empirical cumulative distribution function (ECDF) 
-  of this distribution of deviations. 
+  of these distributions of deviations. 
   % Each ECDF contains 40 data points, one from each independent simulation.
-  The ECDFs of 5 randomly selected centers of 
-  mass are shown in Figure~\ref{fig:offset_ecdfs} (colored lines). We also calculated 
+  The ECDFs of 3 randomly selected COMs
+  are shown in Figure~\ref{fig:offset_ecdfs} (colored lines). The average 
+  of all COM ECDFs is represented by the red line with the 95 \% confidence
+  interval represented by the red error bars. We also calculated 
   the ECDF from the full distributions in Figure~\ref{fig:offset_ensemble_pooled}
   (black line with error bars). We generated error bars that represent the 95\% 
-  confidence intervals, by randomly sampling 40 values (the same as the number 
-  of independent simulations) from the distributions in 
-  Figure~\ref{fig:offset_ensemble_pooled}, then measuring the deviation between
-  the sampled ECDF and the full ECDF. The center of mass ECDFs lie between the
-  error bars of the full ECDF within reason. This provides further evidence that
-  each center of mass moves independently, in random directions when systems
-  quench.
-
-% Sandwiched: (0.019 nm, 0.007 nm, 0.023 radians)
-
-  \begin{figure}[!htb]
-  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.png}
-%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_stds.png}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=0.45\textwidth]{offset_ensemble_stds.png}
-%  \caption{Parallel Displaced}\label{fig:offset_ensemble_stds.png}
-%  \end{subfigure}
-  \caption{There is a narrow spread in the standard deviation of
-  quenched disorder for each independent configuration.}\label{fig:ensemble_stds}
-  \end{figure}
+  confidence intervals, by performing 1000 trials where we randomly sampled 40
+  values (the same as the number of independent simulations) from the distributions in 
+  Figure~\ref{fig:offset_ensemble_pooled}, then measured the deviation between
+  the sampled ECDF and the full ECDF. These error bars are generally smaller than
+  those generated from the 400 COM ECDFs. This is because there is a wider
+  distribution of mean COM deviations than the mean deviations from distributions
+  sampled from the full distribution. The above evidence supports that each quenched
+  configuration is random and mostly independent.
 
@@
   \begin{subfigure}{\textwidth}
+  % BJC15: I don't think it's necessary to put the 3 randomly selected ECDFs in since it
+  % doesn't provide extra information and clutters the figure. Left there for now.
+  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
   \includegraphics[width=\textwidth]{offset_ecdfs.png}
-  \caption{Emperical cumulative distribution functions generated from (a) and
+  \caption{Empirical cumulative distribution functions generated from (a) and
   from simulation ensembles.}\label{fig:offset_ecdfs}
   \end{subfigure}
-  \begin{subfigure}{\textwidth}
-  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
-  \caption{Radial density of select monomer components.}\label{fig:offset_ensemble_regional_density}
-  \end{subfigure}
-  \caption{The distributions of the deviations of head group center of masses
+  \caption{(a) The distributions of the head group COM deviations
   from their idealized positions generated using pooled data from all
@@
   there is equal probability for a head group to displace in the positive
-  or negative $z$, $r$ or $\theta$-direction.}\label{fig:full_ensemble_distributions}
+  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
+  given head group is displaced randomly upon quenching. The ECDF generated from
+  the pooled distributions (black) in (a) agree with the means of the 
+  ECDFs generated from each COM (red). The red error bars are larger than
+  the black error bars since there is a wider distribution of mean COM
+  deviations than the mean deviations of distributions sampled from the full
+  distribution.}\label{fig:full_ensemble_distributions}
+  \end{figure}
+
+  % BJC15: How important is it to prove in the main text (rather than supporting)
+  % that the long systems sample the same distribution as above. Since they were
+  % generated using the same procedure, why should the reader question it?
+
+  The systems that we ran for 400 ns and used for most of our analysis are
+  representative of the long term simulation behavior of any system chosen from the 
+  ensemble. The distributions of standard deviations generated from each of
+  the ensemble trajectories (Figures~\ref{fig:offset_ensemble_stds} 
+  and~\ref{fig:offset_ensemble_means}) are fairly tight with ($\sigma_{\sigma_z}$,
+  $\sigma_{\sigma_r}$, $\sigma_{\sigma_\theta}$) = (0.011 nm, 0.007 nm , 0.022 radians).
+  We analyzed the first 5 ns of the 400 ns ordered parallel displaced
+  configuration and observe the same amount of disorder (based on the $\sigma$ values
+  in Figure~\ref{fig:offset_ensemble_stds}) with indistinguishable 
+  mean values. Additionally, we calculated the radial density of monomer components as a 
+  function of their distance from the pore centers (Figure~\ref{fig:offset_ensemble_regional_density}).
+  All simulations have similar profiles. The distribution of sodium ions near the
+  pore center is relatively noisy since the sodium ions are have much more 
+  translational freedom than the head groups.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{offset_ensemble_stds.png}
+  \caption{}\label{fig:offset_ensemble_stds}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{offset_ensemble_means.png}
+  \caption{}\label{fig:offset_ensemble_means}
+  % BJC15: The mean z-value seems a little silly since it is basically zero except for numerical error I presume
+  % The mean is required to be zero for the calculation to work since columns are randomly displaced.
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
+  %BJC15: I can explicitly define the colors for each system since all the ugly colors come out on top
+  \caption{}\label{fig:offset_ensemble_regional_density}
+  \end{subfigure}
+  \caption{(a) The standard deviation of the distribution of quenched disorder
+  from the first 5 ns of the main ordered parallel displaced system studied in
+  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
+  standard deviations calculated from the ensemble of simulations (histogram). 
+  (b) The mean values of $z$, $r$ and $\theta$ from the first 5 ns of the main
+  system (black dashed line) is in agreement with the distribution of mean values
+  calculated from each simulation in the ensemble. (c) The radial densities of tail
+  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
+  main system simulation trajectory (black lines) and from the ensemble of 
+  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
+  \end{figure}
+
+  We can explain the discrepancies between R-$\pi$ seen experimentally
+  and in simulation using what we have shown in this section. The stacking
+  distance between monomer head groups is too large, likely due to failures
+  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
+  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
+  ordering in the $z$-direction in addition to high degrees of correlation 
+  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
+  which is also likely a consequence of columns that are too highly correlated.
+  If we limit ourselves to standard simulation techniques, it is necessary to 
+  average data generated from ensembles of independent simulation trajectories
+  in order to begin converging on time-averaged descriptions of the system's
+  molecular structure.
+
+  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
+  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
+  % “in between sandwiched and parallel displaced” looks like would be helpful"
+  % BJC15: could move figure to supplemental to save space
+  % BJC15: Added a transition type clause to the beginning of this first sentence
+  % to help with flow. It might be too much though.
+  A secondary conclusion that we've drawn from the evidence in this section is 
+  that the architecture of each column is likely in between our sandwiched
+  and parallel displaced configurations. The parallel displaced configuration 
+  that we have simulated in this paper is an exaggerated manifestation of the 
+  parallel displaced $\pi-\pi$ stacking mode. Not only is the intensity of R-$\pi$
+  calculated from the ensemble of parallel displaced simulations in close agreement
+  with experiment, but the experimental WAXS pattern shows faint off-axis features
+  at the same $q_r$ value as R-double which are only present in simulated patterns
+  generated from parallel displaced configurations. The monomers may prefer to be
+  parallel displaced, but their displacement is likely only slightly shifted, on 
+  the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
+  (See Figure~\ref{fig:between_pd}). In this way, columns can more easily act 
+  independently while maintaining a parallel displaced structure. It is hard to
+  imagine parallel displaced columns, as we have set them up, acting independently 
+  unless we force them to be that way, as we did to create the ensemble of parallel
+  displaced simulations.
+
+  %BJC15: figure in response to Matt
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{pd_36.eps}
+  \caption{}\label{fig:pd_36}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{pd_lt36.eps}
+  \caption{}\label{fig:pd_lt36}
+  \end{subfigure}
+  \caption{Head groups are likely stack in a configuration between sandwiched and
+  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
+  per columns, we placed head groups so the angle, $\theta$, between vectors extending
+  from vertically stacked head groups to the pore center equals 36$\degree$ 
+  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
+  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
+  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
+  configuration.}\label{fig:between_pd}
   \end{figure}
@@
 %  a robust simulated XRD pattern.
-
-  %BJC6: not sure if this should go in supplemental
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.4\textwidth}
-%	  \includegraphics[width=\linewidth]{sandwich_rzplot_highlimit_cbar.png}
-%	  \caption{}\label{fig:simulated_adjusted_colorbar}
-%  \end{subfigure}
-%  \begin{subfigure}{0.4\textwidth}
-%	  \includegraphics[width=\linewidth]{WAXS_raw_adjusted_colorbar.png}
-%	  \caption{}\label{fig:experimental_adjusted_colorbar}
-%  \end{subfigure}
-%  \caption{R-$\pi$ and R-pores are far more intense than the other major reflections in 
-%  the simulated diffraction patterns (a). Here, the colorbar was scaled so that the max is 6x
-%  higher than all other plots.}\label{fig:intense_rpi}
-%  \end{figure}
 

### 2018-09-14 Ben_Manuscripts/structure_paper/Draft.tex
Comments.

@@
 
-  Since the dynamics of this system appear to be quite slow, and consequently most of
-  our analysis has been focused on a small set of quenched configurations whose 
-  structures do not vary significantly with time, we attempted
-  to learn more about their time-averaged structures by studying ensembles of simulations.
+  Since the dynamics of this system are slow, and consequently most of
+  our analysis has been focused on a set of quenched configurations with some structural characteristics that do not 
+  vary significantly with time, we attempted
+  to learn more about their time-averaged structures by studying ensembles of shorter simulations started
+  from more independent initial configurations.
 %  Disorder among head groups in the simulated atomistic systems is largely determined
@@
   We created ensembles of 40 simulations in both the parallel displaced and 
-  sandwiched configurations. We used the same equilibration technique as above 
-  (see section~\ref{section:equilibration}), however we built the initial
+  sandwiched configurations. We used the same equilibration scheme as above 
+  (see section~\ref{section:equilibration}). However, we built the initial
   configurations with randomly displaced columns in the $z$-direction and
-  then stopped their equilibration after 5 ns of unrestrained simulation. We 
-  simulated XRD patterns from the 40 concatenated trajectories. The $q_r$ 
+  looked at the results after 5 ns of unrestrained simulation, which should capture any quenched disorder built in 
+  from the initial configurations. We 
+  then simulated XRD patterns from the 40 trajectories, concatenated together. The $q_r$ 
   cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
   in Figure~\ref{fig:ensemble_XRD}. Qualitatively, the cross-sections
-  of are nearly smooth, with small spikes near $q_r$=0. The data 
-  suggests that the average intensity of R-$\pi$ in sandwiched systems is 
+  of are nearly smooth, with only small spikes near $q_r$=0. These data 
+  %MRS15: for sentence below - qualify about the ensemble?
+  suggest that the average intensity of R-$\pi$ in sandwiched systems is 
   about 3$\times$ higher than that in the parallel displaced configuration. 
+  %MRS16: probably don't want to talk about which combination BEST agrees with the ensemble,
+  %but present the different things that in combination would explain most of the differences.
   Overall, the intensity of R-$\pi$ generated from the parallel displaced 
@@
   % However, I can switch it to sandwiched very easily. The discussion below will remain the same
-
+  %MRS15: I think better to just talk about how much things can be reduced in height.
+If there are OTHER features that look more characteristic of the experiment in parallel displaced, you can talk about those.
   \begin{figure}[!htb]
@@
   \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
-  		   patterns from an ensemble of 40 independent simulations. The maximum 
+  		   patterns from an ensemble of 40 independent simulations, suggesting that much of the extra initial intensity may be due to the starting conditions. The maximum 
   		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
@@
 
-  Independent simulations exhibit similar amounts of quenched disorder. 
+  These short independent simulations exhibit similar amounts of quenched disorder. 
   We pooled the deviations of each head group COM from idealized positions
@@
   The ECDFs of 3 randomly selected COMs
-  are shown in Figure~\ref{fig:offset_ecdfs} (colored lines). The average 
+  are shown in Figure~\ref{fig:offset_ecdfs} to guide the eye (colored lines). The average 
   of all COM ECDFs is represented by the red line with the 95 \% confidence
@@
   the sampled ECDF and the full ECDF. These error bars are generally smaller than
-  those generated from the 400 COM ECDFs. This is because there is a wider
+  those generated from the 400 COM ECDFs, as there is a wider
   distribution of mean COM deviations than the mean deviations from distributions
-  sampled from the full distribution. The above evidence supports that each quenched
-  configuration is random and mostly independent.
+  sampled from the full distribution.
+The similarity between entirely indepdently sampled CDFs and the CDFs from individual independent simulations supports the that each quenched configuration is random and mostly independent.
 
@@
   % doesn't provide extra information and clutters the figure. Left there for now.
+  % MRS15: kind of nice to guide the eye?
   % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
+  %MRS15: 95% is fine.
   \includegraphics[width=\textwidth]{offset_ecdfs.png}
@@
   from their idealized positions generated using pooled data from all
-  frames of each independent configuration is symmetric. This implies that 
+  frames of each independent configuration is symmetric, implying that 
   there is equal probability for a head group to displace in the positive
@@
   % generated using the same procedure, why should the reader question it? 
-
-  The systems that we ran for 400 ns and used for most of our analysis are
+  % MRS15: because they could all collapse to the SAME (or similar) quenched disorder, rather than 
+  % different, mostly independent ones.
+
+  The systems run for 400 ns and used for most of our analysis are
   representative of the long term simulation behavior of any system chosen from the 
@@
   % The mean is required to be zero for the calculation to work since columns are randomly displaced.
+  %MRS15: good point.  Probably can leave that off. 
   \end{subfigure}
@@
   %BJC15: I can explicitly define the colors for each system since all the ugly colors come out on top
+  %MRS15: sounds good.  Maybe a bit narrower lines?
   \caption{}\label{fig:offset_ensemble_regional_density}
@@
 
+  %MRS15: make it more clear that you are now summing up this section.  Perhaps put
+  %subheadings in this section, as I discussed.
   We can explain the discrepancies between R-$\pi$ seen experimentally
@@
   % to help with flow. It might be too much though.
-  A secondary conclusion that we've drawn from the evidence in this section is 
+  A secondary conclusion drawn from the evidence in this section is 
   that the architecture of each column is likely in between our sandwiched
@@
   (See Figure~\ref{fig:between_pd}). In this way, columns can more easily act 
-  independently while maintaining a parallel displaced structure. It is hard to
-  imagine parallel displaced columns, as we have set them up, acting independently 
-  unless we force them to be that way, as we did to create the ensemble of parallel
-  displaced simulations.
-
-  %BJC15: figure in response to Matt
+  independently while maintaining some features of parallel displaced structure. 
+  %MRS15: yeah, cut the last bit.
+
+  %BJC15: figure in response to Matt.  
+  %MRS15: This seems like something for supporting information.
   \begin{figure}[!htb]
@@
   % BJC15: first pass at a brief future work paragraph
+  %MRS15: tweaked.
   Future work, based on what has been learned in this study, may help further improve the 
-  structural agreement between experiment and simulation. We may be able to 
-  modify the GAFF force field or use a different force field in order to better
-  capture the $\pi-\pi$ interactions which draw stacked monomers closer together. 
+  structural agreement between experiment and simulation. 
+  %We may be able to 
+  %modify the GAFF force field or use
+  Force fields explicitly including $\pi-\pi$ interactions may be able to draw stacked monomers closer together. 
   We can study ensembles of long simulations in order to observe more averaged 
-  structure and to create more experimentally consistent XRD patterns. Finally, we can
-  run extremely long simulations (on the order of \SI{}{\micro s}) in order to better 
-  quantify the time scales for large scale rearrangements to occur.
-
-  With the structural understanding gained by these simulations, it will becomes
+  structure and to create more experimentally consistent XRD patterns. Extremely long simulations 
+  (on the order of \SI{}{\micro s}) may be necessary to better 
+  quantify the time scales for large scale rearrangements, and the precise arrangements themselves.
+
+  With the structural understanding gained by these simulations, it will be
   possible to evaluate transport of various solutes within the system, and apply the
   knowledge gained from this study in order to suggest improvements to the
-  existing system as well as to evaluate new unsynthesized LLC systems.
+  existing system, as well as to evaluate new unsynthesized LLC systems.
 

### 2018-09-15 Ben_Manuscripts/structure_paper/Draft.tex
revisions

@@
 \author{Benjamin J. Coscia}
+\author{Joe Yelk}
+\author{Matthew A. Glaser}
+\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
 \author{Richard D. Noble}
@@
 \alsoaffiliation{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
-\author{Joe Yelk}
-\author{Matthew A. Glaser}
-\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
 \author{Xunda Feng}
@@
   and reveal that there exists a composition gradient rather than an abrupt
-  partition between the hydrophilic and hydrophobic regions. 
-  % BJC13: If this is to be included here, it needs some rewording. I allude to
-  % this when talking about the independently moving columns above. 
-  %A caveat is
-  %that the time scales of the dynamics are extremely long for this system, 
-  %resulting in simulated structures that appear too ordered which requires
-  %careful examination of the metastable states observed in order to draw any
-  %conclusions. 
-  %MRS14: OK, let's talk through it.  I feel that this is an important caveat to add so
-  %that people don't think we are claiming more than we are, and therefor should be mentioned
-  % explicitly, rather than the implication left above.
-  The clearer picture of the nanoscopic structure of these membranes provided
-  in this study will enable a better understanding of the mechanisms of small
-  molecule transport within these nanopores.
+  partition between the hydrophilic and hydrophobic regions. A caveat is
+  that the time scales of the dynamics are extremely long for this system, 
+  resulting in simulated structures that appear too ordered which requires
+  careful examination of the metastable states observed in order to draw any
+  conclusions. The clearer picture of the nanoscopic structure of these 
+  membranes provided in this study will enable a better understanding of
+  the mechanisms of small molecule transport within these nanopores.
 
@@
   % BJC5: Note to self -- how to use latex xr : Figure S~\ref{S-fig:monomer_color_coded}
-
-  % MRS8: intro still seems a bit limited, describe more generally
-  % (and briefly!) other things selective membranes are good for. The
-  % paper is primarily about selective membranes, not fracking
-  % water. See elimalech paper for reviews, and add a number of more
-  % citations.
-
-  %MRS14: I feel this introduction spends a bit too much time talking at too general a level.
-The paper introduction to the problem tackled in the paper.
-One simple way to tighten it up would be to improve the connection between the thesis and the data.
-You say that highly selective membranes would be useful, but then don't provide evidence that they are the solution to the problems listed.
-
-  % In order to perform complex separations x, y and z at reduced costs, we need highly selective membranes 
-  % include all descriptions of separation processes into this paragraph
 
@@
   separating contaminants from feed solutions with highly selective membranes,
-  it is is possibl to reduce the number of required membrane passes and post-treatment steps
+  it is possible to reduce the number of required membrane passes and post-treatment steps
   needed for a given filtration process \cite{werber_materials_2016}, thus
@@
   in size and smaller, as well as ions. However the porous architecture of
-  commercially 
-  %MRS15: may be too strong an assertion.
-  %dominant
-  available 
-  membranes lack uniformity which severely impacts their
+  commercially available membranes lack uniformity which severely impacts their
   selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
@@
   % long-term route towards highly selective membranes are those that are nanostructured
-  %MRS15: popilar for separations applications would imply the are getting a larger market share now, 
-  %though my impression is that they are research topics of heavy interest, but not yet that commercially viable.  Check my chainge below.
-  Nanostructured porous membrane materials have become 
-  %increasingly popular
-  an increasingly popular research area for
-  aqueous separations applications because they offer the ability to control pore
-  architecture at the molecular scale, thereby permitting the design of
-  solute-specific separation membranes \cite{humplik_nanostructured_2011}.
-  However their development has been limited by the ability to synthesize and
-  scale 
-  %MRS15: not sure what you mean by ``fundamentally sound technologies''.
-THat the underlying principles are good, but that scaling is hard?
-Fundamentally sound seems to suggest that both principles and scaling are good, but that's not what the implication is.
-  various fundamentally sound technologies. Graphene sheets are atomically
-  thick which results in excellent water permeability but defects during
-  manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
+
+  Nanostructured porous membrane materials have become an increasingly popular
+  research area for aqueous separations applications because they offer the 
+  ability to control pore architecture at the molecular scale, thereby 
+  permitting the design of solute-specific separation membranes 
+  \cite{humplik_nanostructured_2011}. However their development has been 
+  limited by the ability to synthesize and scale various technologies. Graphene
+  sheets are atomically thick which results in excellent water permeability but
+  defects during manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
   Molecular dynamics (MD) simulations of carbon nanotubes show promise
@@
 
-%BJC13: You can stop here, I haven't changed anything below.
-
 %  This makes overcoming the well-known 
@@
 
-%MRS8: preliminary evidence has shown they may be?  It's more than a guess.
   Preliminary evidence has shown that crosslinked lyotropic liquid crystal
@@
   which are detrimental to membrane permeability. This domain scale misalignment
-  have inhibited further development of the this technology, and research efforts
+  had inhibited further development of this technology, and research efforts
   were focused on the Q\textsubscript{I} phase, whose geometry does not require
-  alignment~\cite{dischinger_papers}.
+  alignment~\cite{zhou_new_2007}.
 
@@
   substrates since hexagonal mesophases preferentially anchor perpendicular to
-  both surfaces\cite{feng_thin_2016}.
-%  the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
-  %MRS8: maybe say what it is, not just what it's named? 
-  Current experimental efforts are focused on extending the method to the
-  H\textsubscript{II} phase and characterizing the performance of these newly
-  aligned systems.
+  both surfaces\cite{feng_thin_2016}. Current experimental efforts are focused
+  on extending the method to the H\textsubscript{II} phase and characterizing
+  the performance of these newly aligned systems.
 
@@
 	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
-	exhibits wedge-like character. (d) Monomers stack on top of each other with
-	short range order and assemble into pores. (e) The hydrophilic head groups 
-	(blue) facing towards the pore center. The pores assemble into hexagonally
-	packed columnar mesophases.}~\label{fig:assembly}
+	exhibits wedge-like character. (d) Monomers stack on top of each other to
+	create columns with short range order then assemble into pores with  
+	hydrophilic head groups (blue) face towards the pore center. (e) The 
+	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
   \end{figure}
@@
   % BJC14: (5) justify need for simulations
-  % BJC14: dishchinger example seems like a good thing to bring up since they 
-  % explicitly state in the paper that they need a better understanding of
-  % transport
+
   Our current understanding of the molecular details of LLC membranes'
@@
 
-  %BJC14: nothing new after this point
-
   A molecular-level understanding of LLC membrane structure, enabled by
@@
 	\AA$^{-1}$, corresponding to a real space separation of 3.7 {\AA}. Previous
-	work~\cite{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
+	work attributes this reflection to $\pi$-$\pi$
 	stacking between aromatic rings in the direction perpendicular to the membrane
@@
 	\item \textit{R-pores}: The final feature corresponds to the spacing
-	and symmetry of the pore columns. 
-        %d\textsubscript{100} plane. This plane is geometrically
-        %related the distance between pores.
-	The feature, which we named R-pores, is characterized by reflections along the
-	equatorial axis defined by $q_z$ = 0. The spacing between dots is indicative of
-	the hexagonal symmetry of the packed pores. We observe the same information
-	with higher resolution using SAXS (Fig.~\ref{fig:SAXS}).
+	and symmetry of the pore columns. The feature, which we named R-pores, 
+	is characterized by reflections along the equatorial axis defined by $q_z$ = 0.
+	The spacing between dots is indicative of the hexagonal symmetry of the 
+	packed pores, and the location of the leading peak (closest to $q_r$ = 0)
+	is related to the distance between pores. We observe the same information
+	with higher resolution by looking at the same system's 1D SAXS pattern 
+	(Fig.~\ref{fig:SAXS}).
 
@@
 
-  	We are careful to avoid the term 'layers' since many liquid crystalline systems
+  	We are careful to avoid the term ``layers" since many liquid crystalline systems
  	have long range order in 1 or 2 spatial dimensions and short range order in 	
@@
         %see if there is any
-	meaningful structural difference between a "dry" and a "wet" system.
+	meaningful structural difference between a ``dry" and a ``wet" system.
 
@@
   calling for a more efficient way to build the system. Previous work has shown
-  a coarse-grained model self assemble into the H\textsubscript{II} phase
+  a united-atom model self assemble into the H\textsubscript{II} phase
   configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
@@
   %MRS13: Would be nice to say we put the scripts on GitHub.  Additional details about which scripts can be in supporting.
-  These initial structures may result in equilibration into slowly-intercoverting metastable states, an issue we will address later in the paper. 
-  % BJC5: This needs to be modified to reflect columnar build procedure
+  These initial structures may result in equilibration into slowly-intercoverting
+  metastable states, an issue we will address later in the paper.
+
   \begin{figure}[!htb]
@@
   configurations. The initial distance between pores, within a wide range, also has 
-  little effect on the the equilibrated structure. However, one should not start them
+  little effect on the equilibrated structure. However, one should not start them
   too close or there will be high energy repulsions during early equilibration. We 
@@
   explored three different initial monomer spacings. The first is exactly
-  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
-  the z-direction. We also extensively explored a second system with an initial spacing of 5
+  equal to R-$\pi$ with monomers placed so aromatic rings stack 3.7 \AA~apart in
+  the $z$-direction. We also extensively explored a second system with an initial spacing of 5
   \AA. We briefly explored a third system with an initial spacing of 10
@@
 
-  The number of columns per pore is unknown, as stated in question
+  The number of columns per pore is unknown, as stated in Question
   (\ref{point:monomernum}). We tested configurations constructed with a varied
@@
   \subsection{Equilibration}\label{section:equilibration}
+
   We developed equilibration schemes for creating dry and wet configurations.
@@
   Gaussian spheres of electron density whose maximum and width are defined by
-  each atom's atomic number electronic radius respectively. A three dimensional
-  Fourier transform (FT) of the array of electron density results in a three
+  each atom's atomic number and electronic radius respectively. A three dimensional
+  Fourier transform of the array of electron density results in a three
   dimensional structure factor which represents the unit cell in reciprocal
@@
   still misaligned with respect to the $xy$ plane. To account for this, we averaged
-  2D slices of the structure factor at all angles about $|\mathbf{q}| = (0, 0, z)$.
+  2D slices of the structure factor at all angles about $\mathbf{q} = (0, 0, z)$.
 
@@
   \includegraphics[width=\textwidth]{saxs_xsection.png}
-  \caption{R-spots}\label{fig:saxs_xsection}
+  \caption{R-pores}\label{fig:saxs_xsection}
   \end{subfigure}
@@
   within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
-  simulated spectra overlap with R-$\pi$ in that region. in those regions in all cases. (b) We
+  simulated spectra overlap with R-$\pi$ in those regions in all cases. (b) We
   measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
@@
   the R-alkanes region. We took the intensity of R-spots as the average of the 
-  peak intensities near 37 and 143$\degree$. (d) We measured the intensity of 
+  peak intensities near -37 and -143$\degree$. (d) We measured the intensity of 
   R-pores by measuring the height of the d\textsubscript{100} peak (the leading
@@
   $\delta(\mathbf{r})$ is the Dirac delta function\cite{kuriabova_linear_2010}.
-  We applied equation \ref{eqn:correlation} in three dimensions and then
+  We applied Equation \ref{eqn:correlation} in three dimensions and then
   extracted one dimensional distribution functions using slices of the grid
@@
   We measured the one dimensional pair distribution function, $g(z)$, between centers 
-  of masses of aromatic head group rings along the z-axis (perpendicular to
+  of masses (COM) of aromatic head group rings along the z-axis (perpendicular to
   the membrane plane). We averaged all 1D $z$-directional slices of the full 3D 
@@
   We calculated the radius as the sum of the longest C-C distance within a phenyl 
-  ring (2.8~\AA) and two times the carbon atom radius (0.7~\AA). % citation
+  ring (2.8~\AA) and two times the carbon atom electronic radius (0.7~\AA)
+  ~\cite{slater_atomic_1964}. % citation
 
@@
   (see Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
-  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
-  %MRS13: I assume a linear least squares fit?  Be precise so it's reproducible.
+  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$,
+  using the python package \texttt{scipy.optimize.curve\_fit}~\cite{oliphant_python_2007},
   to a decaying exponential function of the form:
@@
   of L as the square root of the diagonal entry of the covariance matrix of 
-  optimized fit parameters.  %BJC6: reference scipy curve_fit?
+  optimized fit parameters.
 
@@
   %are too large to extract a precise value of $\mathit{d}_equil$. Instead, 
-  We fit a decaying sinusoidal function to $g(z)$ of the form:
+  We fit a decaying sinusoidal function (using \texttt{scipy.optimize.curve\_fit}) to 
+  $g(z)$ of the form:
   \begin{equation}
@@
   In order to gain a deeper understanding of discrepancies between the experimental and
-  and simulated R-$\pi$ reflection, we used a simplified model where we 
-  represent each monomer as a single point scatterer located at the center of mass
+  simulated R-$\pi$ reflection, we used a simplified model where we 
+  represent each monomer as a single point scatterer located at the COM
   of its head group. In order to make a system approximately similar to our equilibrated 
@@
   simulation. We measured thermal disorder by calculating the standard deviation of 
-  the distribution of head group center of mass positions from their average positions.
+  the distribution of head group COM positions from their average positions.
   We measured quenched disorder by calculating the standard deviation of the distribution
-  of head group center of masses from their idealized average positions. In the 
-  $z$-direction, we measured the deviation of the head group center of masses from an
+  of head group COMs from their idealized average positions. In the 
+  $z$-direction, we measured the deviation of the head group COMs from an
   equally spaced column of head groups. In the $xy$ plane, we calculated the standard 
@@
   distribution at each point along the column the same standard deviation, 
-  $\sigma_z$ and we defined a covariance matrix such that the covariance, $v$, of
+  $\sigma_z$, and we defined a covariance matrix such that the covariance, $v$, of
   the distance, $d$, between scatterers decays exponentially from $v$ according
@@
   Our simulations best support a model built with 5 monomer columns per pore based on
-  the measured equilibrated pore-to-pore distances. To discern the composition of
-  the monomer layers, addressing Question \ref{point:monomernum} above, we ran
+  the measured equilibrated pore-to-pore distances. To discern the density of
+  monomer columns in each pore, addressing Question \ref{point:monomernum} above, we ran
   simulations of systems created with 4--8 columns per pore. We built systems in both
@@
   around the $q_z$-axis, meaning there are fewer samples as $q_r$ approaches 0.
-  The amount of samples required to to converge along the $q_z$ axis is analyzed
-  in Supporting Information section S-\ref{S-section:xrd_noise}.  More
-  importantly, our simulations do not appear to be long enough to sample truly
+  More importantly, our simulations do not appear to be long enough to sample truly
   independent configurations within their respective metastable basins (see
   section~\ref{section:slow_dynamics}), meaning we must take care in interpreting
-  the results of the XRD. The simulated patterns generated for all systems
-  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
-
-  % BJC10: to be reformatted : add captions. Maybe shift experimental pattern to (a)
-  % BJC10: be more terse in main caption. Add references to sections
+  the results of the XRD. The amount of independent configurations required to 
+  converge along the $q_z$ axis is analyzed in Supporting Information, 
+  Section S-\ref{S-section:xrd_noise}. The simulated patterns generated for all
+  systems studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
+
   \begin{figure}[!htb]
@@
   \end{tabular}
-  %MRS12: question: is the normalization for the simulated systems the same, no matter if disordered, etc.  If not chosen to be exactly the same, how different are they?
-  %BJC12: Are you asking what the normalization constant is that I divide the patterns by for each system? I'll have to check. 
   \caption{The simulated XRD patterns of the systems tested, normalized so that
@@
 	  reflections that are slightly lower than experiment. R-double does not appear
-	  in any simulated patterns, and thus has no measurable intensity.}
+	  in any simulated patterns, and thus has no measurable intensity. In terms of 
+	  the locations of the reflections, R-pores, R-alkanes and R-spots appear at $q$
+	  values that close to experiemnt, while R-$\pi$ appears at a significantly lower
+	  $q$ value than experiment.}
   \label{table:relative_intensities_300K} 
@@
   simulations.  We reach this conclusion because alkane parameters in GAFF and
-  AMBER forcefields generally reproduce data well.~\cite{original_gaff_paper} 
-  %MRS12: Citation is: https://doi.org/10.1002/jcc.20035  could also cite: https://pubs.acs.org/doi/pdf/10.1021/ct200731v
-
-  %MRS12: below - say what appears close means?  radius of max is X vs Y.
+  AMBER forcefields generally reproduce data well.~\cite{wang_development_2004,caleman_force_2012}
+
   R-alkanes appears close to its expected location. In all cases, the maximum
@@
   estimate its location, appears at a $|\mathbf{q}|$ value that is, at most,
-  3.5\% higher than higher than experiment. 
-  %MRS12: different pass?
-Though need to specify WHAT the error is.
-Can't be intensity, since that is what we are normalizing by, so is it LOCATION of the intensity?
-Also, need to verify the statement is correct.
-Could still good languange if the conclusion was that the binning error was similar in size to errors in the location R-alkane.
-  %BJC12: I use the maximum intensity of R-alkanes along the q_r axis at qz=0 to determine its location.
-  The error in the simulated diffraction patterns is less than the error due
-  binning in each frequency direction, so was not further investigated. 
-  %We expect that the exact location of R-alkanes will not be perfect in our simulations
-  %since the simulated diffraction patterns are interpolated between a finite number of
-  %bins in each frequency dimension. 
-  %We can achieve higher resolution with a larger
-  %system size, however we are satisfied with the packing distances shown by our simulations.
-  %BJC11: I could integrate a 3D correlation function to get a better value.
-  %MRS12: saying ``we are satisfied'' opens to claims that reviwers say ``well, I'm not''.  Pass at this above.
+  3.5\% higher than higher than experiment. The error in the simulated 
+  diffraction patterns is less than the error due binning in each frequency
+  direction, so was not further investigated.
 
@@
   crystalline domains and the pore-to-pore distances fluctuate more over long
-  time scales. 
-  % BJC11: Using simple systems, I can show that more highly fluctutating pore-to-pore
-  % distances will decrease the intensity of R-pores. I don't think its worth getting
-  % into in the main text. It's the same idea as how increased z-noise decreases the intensity of R-pi
-  % BJC11: I also think that domain misalignment in the z-direction contributes. If you
-  % imagine a hexagonal array of pores aligned along the z-axis, then rotate that axis
-  % so it has an x and y component, then there will be constructive interference perpendicular
-  % to that axis at non-zero qz values. That is why R-pores is arced. It's a different
-  % type of broadening than R-pi - I think
-  % BJC11: I don't think a deep dive into this is worth it. It's dependent on things
-  % unrelated to the actual pore structure.
-  % MRS12:  Agreed. Rephrased a bit.
-  The agreement in intensity in R-pores obtained here is sufficient for this
+  time scales. The agreement in intensity in R-pores obtained here is sufficient for this
   study because this intensity is primarily controlled by longer-range
@@
   The intensity of R-spots is close to experiment when generated from any of
-  our simulated systems. We measured the intensity of R-spots by radially integrating the simulated
-  diffraction pattern between $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$
-  (between 4 and 4.5 $\AA$ in real space) and then locating and recording the
-  intensity of the appropriate peaks in the resulting distribution. Because the
-  R-spots reflection is difficult to distinguish visually as it appears at the
-  same $|\mathbf{q}|$ as R-alkanes, we calculate the intensity of R-spots by
-  assuming that its $q_z$ location should be roughly in line with the
-  experimental R-double, half the $q_z$ distance of R-$\pi$).
-
-  %MRS12: here I'm going to break the rule of the thesis statement, since it reads strangely to have thesis, contradition, repeat thesis, there isn't any evidence. But it flows OK this way.   
-  %R-spots is most likely a result of ordered packing of the monomer's alkyl tails. 
+  our simulated systems. We measured its intensity as outlined in Section~\ref{method:xrd}.
+
+%  BJC16: moved to methods
+%  We measured the intensity of R-spots by radially integrating the simulated
+%  diffraction pattern for $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$
+%  (between 4 and 4.5 $\AA$ in real space) and then locating and recording the
+%  intensity of the appropriate peaks in the resulting distribution. Because the
+%  R-spots reflection is difficult to distinguish visually as it appears at the
+%  same $|\mathbf{q}|$ as R-alkanes, we calculate the intensity of R-spots by
+%  assuming that its $q_z$ location should be roughly in line with the
+%  experimental R-double, half the $q_z$ distance of R-$\pi$.
+
   Previous literature has attributed the R-spots reflection in this particular
   WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
-  We measured the tilt angle of the alkane chains of the 280K system by measuring
+  We measured the tilt angle of the alkane chains of the 280 K system by measuring
   the angle made by the vector extending from top to bottom of each tail with
@@
   tilt relative to the $xy$ plane to an angle statisically indistinguishable from
-  zero. (See Section S-TBD). 
-  %Similar lack of more than a statistically negligible
-  %tilt occured when we performed the simulations with a number of other starting
-  %configurations, obtaining similar results. 
-  %MRS12: I know we discussed this earlier; there were a number of things that were done to verify this results was consistent, and I think that a rief summary would help. 
-  %BJC12: It was primarily us trying to induce tilt by equilibrating with position restraints. I'm trying to think of what else we might have done. I changed the last sentence for now
+  zero (See Section~S-\ref{S-section:tail_tilt}).
 
@@
 
-%  The Evidence from the simulations strongly suggests that the R-spots signal
-% is not a 
-%  result of alkane chain tilt.
-
   The evidence from simulations strongly suggest that the source of
@@
   of masses of the first four tail atoms of all tails (Figure
-  \ref{fig:centroids}). We measured the angle between each center of
-  mass and its nearest neighbor center of masses with respect to the
+  \ref{fig:centroids}). We measured the angle between each COM
+  and its nearest neighbor COMs with respect to the
   $xy$ plane of the membrane. We see distinct peaks in the
@@
 % evident when you look at the simulated XRD patterns)
-  300K have qualitative and quantitative differences from experiment.
+  300 K have qualitative and quantitative differences from experiment.
   The reflections appear at lower $q_z$ values, they
@@
 %  (Table~\ref{table:relative_intensities_300K}).
+
+  \subsubsection*{Distance and correlation between stacked monomer head groups}
 
@@
   basins at the high part of that range and are on average 0.2 and 0.3 \AA~more
-  distant. This behavior is
-  not surprising since GAFF models atoms as point charges and  % BJC11: need reference %MRS12: just cite the GAFF paper.
+  distant. This behavior is not surprising since GAFF models atoms as point charges and
   does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
-  it more energetically favorable for the monomers to stack closer together.  It
-  is also possible that the tails prevent close stacking of monomer head groups
+  it more energetically favorable for the monomers to stack closer together ~\cite{wang_development_2004}.
+  It is also possible that the tails prevent close stacking of monomer head groups
   and we do not achieve the timescales necessary for them to rearrange into a
-  necessarily more tightly packed configuration. However, we equilibrated the
-  system at 500 K then annealed it to 300 K in an attempt to coerce the tails into
-  a more tightly packed configuration, but we saw no improvement in packing
-  distance over our 300 K models. See section S-TBD for details.
+  necessarily more tightly packed configuration. We equilibrated the
+  system at 500 K then annealed it to 300 K in an attempt to coerce the tails
+  into a more tightly packed configuration. Before annealing and in order to
+  stabilize the hexagonal phase at 500 K, we placed harmonic restraints with 
+  force constants of 1000 $kJ\ mol^{-1}\ nm^{-2}$ between head group COMs
+  within each column as well as between head group COMs in
+  adjacent columns. We saw no improvement in packing distance over our 300 K
+  models (See further discussion in section~\ref{section:slow_dynamics}).
 
@@
   R-$\pi$ between experiment and simulation is less than one bin size
-  (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). The more
-  signficant difference between the two cross-sections is their maximum intensity
+  (Figures~\ref{fig:exp_zsection_fit} and~\ref{fig:sim_zsection_fit}). The more
+  significant difference between the two cross-sections is their maximum intensity
   which we study in more detail below.
@@
   \end{table}
+
+  \subsubsection*{Shape and Intensity of the $q_r$ cross-section of R-$\pi$}
 
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.49\textwidth}
   \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.49\textwidth}
   \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
@@
   with varying amounts of statistical correlation between columns. In the low
-  limit, the center of mass of columns are situated at the same $z$-coordinate.
+  limit, the COM of columns are situated at the same $z$-coordinate.
   We allow increasing independence of columns by randomly shifting each column in
@@
   3D correlation function. When we include all $z$-slices in $g(z)$ for our
-  system, the function shows oscillatory behavior and the correlation length
+  system, rather than restricting it to those $z$-slices within 2.1 \AA of the
+  center of the correlation function (Section~\ref{section:correlation_length}),
+  the function shows oscillatory behavior and the correlation length
   nearly triples to 12.4 $\pm$ 0.7 \AA. (Figure~\ref{fig:z_correlation_fullbox}).
@@
 
-  Since the dynamics of this system are slow, and consequently most of
-  our analysis has been focused on a set of quenched configurations with some structural characteristics that do not 
-  vary significantly with time, we attempted
-  to learn more about their time-averaged structures by studying ensembles of shorter simulations started
-  from more independent initial configurations.
-%  Disorder among head groups in the simulated atomistic systems is largely determined
-%  by each system's quenched configuration. We observe rapid reorganization of our 
-%  initial configurations into configurations with quenched disorder that does not
-%  vary significantly for the remainder of the
-%  simulation time. For that reason, 
-  We created ensembles of 40 simulations in both the parallel displaced and 
-  sandwiched configurations. We used the same equilibration scheme as above 
-  (see section~\ref{section:equilibration}). However, we built the initial
-  configurations with randomly displaced columns in the $z$-direction and
-  looked at the results after 5 ns of unrestrained simulation, which should capture any quenched disorder built in 
-  from the initial configurations. We 
-  then simulated XRD patterns from the 40 trajectories, concatenated together. The $q_r$ 
-  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
-  in Figure~\ref{fig:ensemble_XRD}. Qualitatively, the cross-sections
-  of are nearly smooth, with only small spikes near $q_r$=0. These data 
-  %MRS15: for sentence below - qualify about the ensemble?
-  suggest that the average intensity of R-$\pi$ in sandwiched systems is 
-  about 3$\times$ higher than that in the parallel displaced configuration. 
+  \subsubsection*{Quenched disorder in ensembles of configurations}
+
+  Since the dynamics of this system are slow, and consequently most
+  of our analysis has been focused on a set of quenched configurations
+  with some structural characteristics that do not vary significantly
+  with time, we attempted to learn more about their time-averaged 
+  structures by studying ensembles of shorter simulations started
+  from more independent initial configurations. We created ensembles
+  of 40 simulations in both the parallel displaced and sandwiched 
+  configurations. We used the same equilibration scheme as above 
+  (see section~\ref{section:equilibration}). However, we built the 
+  initial configurations with randomly displaced columns in the 
+  $z$-direction and looked at the results after 5 ns of unrestrained
+  simulation, which should capture any quenched disorder built in 
+  from the initial configurations. We then simulated XRD patterns 
+  from the 40 trajectories, concatenated together. The $q_r$ 
+  cross-sections of R-$\pi$ generated from the two concatenated 
+  trajectories are shown in Figure~\ref{fig:ensemble_XRD}. 
+  Qualitatively, the cross-sections of are nearly smooth, with only
+  small spikes near $q_r$=0. These data suggest that the average 
+  intensity of R-$\pi$ in the ensemble of sandwiched systems is 
+  about 3$\times$ higher than that in the ensemble of parallel displaced
+  configurations. Compared to our long simulations, the intensity of R-$\pi$
+  generated from ensembles of short simulations, decreases by a factor of 3
+  and by a factor of 2 for the sandwiched and parallel displaced configurations respectively. 
   %MRS16: probably don't want to talk about which combination BEST agrees with the ensemble,
@@
 If there are OTHER features that look more characteristic of the experiment in parallel displaced, you can talk about those.
+
   \begin{figure}[!htb]
@@
   (black line with error bars). We generated error bars that represent the 95\% 
-  confidence intervals, by performing 1000 trials where we randomly sampled 40
+  confidence intervals by performing 1000 trials where we randomly sampled 40
   values (the same as the number of independent simulations) from the distributions in 
@@
   distribution of mean COM deviations than the mean deviations from distributions
-  sampled from the full distribution.
-The similarity between entirely indepdently sampled CDFs and the CDFs from individual independent simulations supports the that each quenched configuration is random and mostly independent.
+  sampled from the full distribution. The similarity between entirely independently
+  sampled ECDFs and the ECDFs from individual independent simulations supports 
+  the hypothesis that each quenched configuration is random and mostly independent.
 
@@
   \centering
-%  \begin{subfigure}{\textwidth}
-%  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.png}
-%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_pooled.png}
-%  \end{subfigure}
   \begin{subfigure}{\textwidth}
@@
   \begin{subfigure}{\textwidth}
-  % BJC15: I don't think it's necessary to put the 3 randomly selected ECDFs in since it
-  % doesn't provide extra information and clutters the figure. Left there for now.
-  % MRS15: kind of nice to guide the eye?
   % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
@@
   from their idealized positions generated using pooled data from all
-  frames of each independent configuration is symmetric, implying that 
+  frames of each independent configuration are symmetric, implying that 
   there is equal probability for a head group to displace in the positive
@@
 
-  % BJC15: How important is it to prove in the main text (rather than supporting)
-  % that the long systems sample the same distribution as above. Since they were
-  % generated using the same procedure, why should the reader question it? 
-  % MRS15: because they could all collapse to the SAME (or similar) quenched disorder, rather than 
-  % different, mostly independent ones.
-
-  The systems run for 400 ns and used for most of our analysis are
-  representative of the long term simulation behavior of any system chosen from the 
-  ensemble. The distributions of standard deviations generated from each of
-  the ensemble trajectories (Figures~\ref{fig:offset_ensemble_stds} 
-  and~\ref{fig:offset_ensemble_means}) are fairly tight with ($\sigma_{\sigma_z}$,
-  $\sigma_{\sigma_r}$, $\sigma_{\sigma_\theta}$) = (0.011 nm, 0.007 nm , 0.022 radians).
+  The systems that we simulated for 400 ns and then used for most of our
+  analysis are representative of the long term simulation behavior of any
+  system chosen from the ensemble. The distributions of standard deviations 
+  generated from each of the ensemble trajectories 
+  (Figures~\ref{fig:offset_ensemble_stds} and~\ref{fig:offset_ensemble_means}) 
+  are fairly tight with ($\sigma_{\sigma_z}$, $\sigma_{\sigma_r}$, $
+  \sigma_{\sigma_\theta}$) = (0.011 nm, 0.007 nm , 0.022 radians).
   We analyzed the first 5 ns of the 400 ns ordered parallel displaced
-  configuration and observe the same amount of disorder (based on the $\sigma$ values
-  in Figure~\ref{fig:offset_ensemble_stds}) with indistinguishable 
-  mean values. Additionally, we calculated the radial density of monomer components as a 
-  function of their distance from the pore centers (Figure~\ref{fig:offset_ensemble_regional_density}).
+  configuration and observed the same amount of disorder (based on the $\sigma$
+  values in Figure~\ref{fig:offset_ensemble_stds}) with indistinguishable 
+  mean values. Additionally, we calculated the radial density of monomer
+  components as a function of their distance from the pore centers 
+  (Figure~\ref{fig:offset_ensemble_regional_density}).
   All simulations have similar profiles. The distribution of sodium ions near the
-  pore center is relatively noisy since the sodium ions are have much more 
+  pore center is relatively noisy since the sodium ions have much more 
   translational freedom than the head groups.
@@
   \caption{}\label{fig:offset_ensemble_means}
-  % BJC15: The mean z-value seems a little silly since it is basically zero except for numerical error I presume
-  % The mean is required to be zero for the calculation to work since columns are randomly displaced.
-  %MRS15: good point.  Probably can leave that off. 
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
-  %BJC15: I can explicitly define the colors for each system since all the ugly colors come out on top
-  %MRS15: sounds good.  Maybe a bit narrower lines?
   \caption{}\label{fig:offset_ensemble_regional_density}
@@
   standard deviations calculated from the ensemble of simulations (histogram). 
-  (b) The mean values of $z$, $r$ and $\theta$ from the first 5 ns of the main
-  system (black dashed line) is in agreement with the distribution of mean values
-  calculated from each simulation in the ensemble. (c) The radial densities of tail
+  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
+  system trajectory (black dashed line) is in agreement with the distribution of mean values
+  calculated from each simulation in the ensemble (histogram). The mean values of $z$
+  are necessarily 0 so they are not plotted. (c) The radial densities of tail
   atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
@@
 
-  %MRS15: make it more clear that you are now summing up this section.  Perhaps put
-  %subheadings in this section, as I discussed.
+  \subsubsection*{The implications of the new-found understanding of R-$\pi$}
+
   We can explain the discrepancies between R-$\pi$ seen experimentally
@@
 
-  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
-  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
-  % “in between sandwiched and parallel displaced” looks like would be helpful"
-  % BJC15: could move figure to supplemental to save space
-  % BJC15: Added a transition type clause to the beginning of this first sentence
-  % to help with flow. It might be too much though.
   A secondary conclusion drawn from the evidence in this section is 
@@
   the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
-  (See Figure~\ref{fig:between_pd}). In this way, columns can more easily act 
+  (See Figure~S-\ref{S-fig:between_pd}). In this way, columns can more easily act 
   independently while maintaining some features of parallel displaced structure.
-  %MRS15: yeah, cut the last bit.
-
-  %BJC15: figure in response to Matt.  
-  %MRS15: This seems like something for supporting information.
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{pd_36.eps}
-  \caption{}\label{fig:pd_36}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{pd_lt36.eps}
-  \caption{}\label{fig:pd_lt36}
-  \end{subfigure}
-  \caption{Head groups are likely stack in a configuration between sandwiched and
-  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
-  per columns, we placed head groups so the angle, $\theta$, between vectors extending
-  from vertically stacked head groups to the pore center equals 36$\degree$ 
-  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
-  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
-  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
-  configuration.}\label{fig:between_pd}
-  \end{figure}
 
@@
   barrier that prevents rotation of carboxylate groups attached to phenyl rings
-  since the group extends the system's $\pi$ conjugation (citation) (See Figure
+  since the group extends the system's $\pi$ conjugation ~\cite{carey_organic_2011} (See Figure
   S-\ref{S-fig:carboxylate_dihedral_rb}), which is significant even considering
-  possible overestimates of the barrier height in the classial force field. 
+  possible overestimates of the barrier height in the classical force field. 
 %  
@@
   the phenyl ring is oriented $\pm 15 \degree$ with respect to the vector
-  extending from the carboxylate carbon to the pore center (Figure
+  extending from the head group COM to the pore center (Figure
   ~\ref{fig:rotated_monomers_rzplot_norestraints}). Every other monomer layer is
@@
   may be the most favorable way for them to pack. This configuration is only
-  stable for a few nanoseconds R-double quickly fades. 
+  stable for a few nanoseconds but R-double quickly fades. 
   %MRS12: seems like unnecssary speculation below, since there are a lot of cancelling affects. 
@@
   $z$-direction, but instead form pairs that stack less than 3.7~\AA~apart, with
-  center of masses are spaced 7.4 \AA~ from neighboring pairs of monomers (Figure
+  COMs that are spaced 7.4 \AA~ from neighboring pairs of monomers (Figure
   ~\ref{fig:staggered_rzplot_norestraints}). 
@@
   evidence from QM studies of stacked $\pi-\pi$ systems that such uneven stacking
-  could be energetically stable.~\ref{tauer_beyond_2005}
+  could be energetically stable.~\cite{tauer_beyond_2005}
 
@@
   monomer head group below can just as easily share a water molecule with a head
-  group below itself. In this scenario, the centers of each pair are 2 times the
+  group below itself. In this scenario, the COMs of each pair are 2 times the
   $\pi$-stacking distance apart which would lead to R-double (much like the
@@
   that membranes are less likely to assemble under completely dry
-  conditions~\cite{personal_communication_with_mike_mcgrath}, supporting the idea
+  conditions, supporting the idea %~\cite{personal_communication_with_mike_mcgrath} <- BJC16: what do I do with this?
   that the ``dry'' structures do absorb some water. This detail may therefore be
@@
   %MRS13: are these hydrophulic/hydrophopic LC?  Once with electrostatic driving forces are likely 
-  % to be even slower.  We measured the diffusion constants of
-  monomers in each of the systems we studied (See Table
-  S-\ref{S-table:msd}) and learned that they are all on the order of
+  % to be even slower.  
+  We measured the diffusion constants of monomers in each of the systems we
+  studied (See Table S-\ref{S-table:msd}) and learned that they are all on the order of
   $10^{-14}~m^2/s$. However, since on this timescale, no monomers move
@@
   Consequently, there is not enough movement on the timescales we simulated for the system to 
-  consistently reach a definative equilibrium structure.
+  consistently reach a definitive equilibrium structure.
   %MRS13:removed phrase, since long time scale does not guarantee closer to experiment. 
@@
   equilibrate to a stacking distance that is too large compared to experiment. 
-  While this may be in large part due to the forcefield's inability to model aromatic
+  While this may be in large part due to the force field's inability to model aromatic
   interactions, it is also possible that the monomer tails do have enough time to pack 
@@
 
-  The ether dihedrals become decorrelated on a reasonable timescale when the temperature
-  is raised. At 300K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
-  not cross the x-axis until $\sim$105 ns meaning that tails fully rotate on average about 
+  The ether dihedrals become decorrelated on a reasonable timescale when we raise
+  the system temperature. At 300 K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
+  not cross the $x$-axis until $\sim$105 ns meaning that tails fully rotate on average about 
   4 times over the course of the 400 ns that we studied. Additionally, the correlation 
@@
   does not improve packing in our model. In the ideal case, if all monomers stacked 
-  3.7 \AA~ apart, the z-dimension of our unit cell should be 7.4 nm. In the ordered basin, 
+  3.7 \AA~ apart, the $z$-dimension of our unit cell should be 7.4 nm. In the ordered basin, 
   sandwiched system studied in this paper, the $z$-dimension of the unit cell equilibrated 
@@
   \end{subfigure}
-  \caption{}\label{fig:dihedrals}
+  \caption{The outer tail ether dihedrals become decorrelated on a reasonable
+  timescale when we raise the system temperature. (a) The dihedrals do not
+  become decorrelated for ca. 100 ns when the system is equilibrated at 300 K.
+  (b) The ether dihedrals become decorrelated after 11 ns when the temperature
+  of the system is increased to 500 K.}\label{fig:dihedrals}
   \end{figure}
@@
   relationship using the collective diffusion model\cite{liu_collective_2013} 
-  (See section S~\ref{S-fig:conductivity}). The values calculated by the 
+  (See section S-\ref{S-fig:conductivity}). The values calculated by the 
   collective diffusion model agree with Nernst-Einstein values within error, 
@@
 
-  The calculated value of ionic conductivity is 5x higher than experiment because 
+  The calculated value of ionic conductivity is 5 times higher than experiment because 
   we simulated infinitely long, aligned pores. The ionic conductivity measurement 
@@
 
-  Experimentally, membranes are crosslinked for mechanical stability before use. We applied 
+  Experimentally, membranes are cross-linked for mechanical stability before use. We applied 
   our cross-linking algorithm to equilibrated sandwiched and parallel
@@
   configuration and decreases in the parallel displaced configuration, however the 
-  values of cross-linked configurations fall within uncertainty of their un-crosslinked
+  values of cross-linked configurations fall within uncertainty of their un-cross-linked
   counterparts. The correlation length decreases in both systems, 
@@
   configurations contain a high level of dependence between monomer columns.
-  Finally, we observed that our model can only produce R-double when we add 
-  small amounts of water to the system. This observation has possible implications
-  for the reproducibility of the experimental results from Feng et al. since they
-  claim that their membrane is completely dry.
+  We can learn more about the time averaged structure of these systems by studying
+  ensembles of independent simulations. Finally, we observed that our model can 
+  only produce R-double when we add small amounts of water to the system. This 
+  observation has possible implications for the reproducibility of the experimental
+  results from Feng et al. since they claim that their membrane is completely dry.
 
@@
 
-  % BJC15: first pass at a brief future work paragraph
-  %MRS15: tweaked.
-  Future work, based on what has been learned in this study, may help further improve the 
-  structural agreement between experiment and simulation. 
-  %We may be able to 
-  %modify the GAFF force field or use
-  Force fields explicitly including $\pi-\pi$ interactions may be able to draw stacked monomers closer together. 
-  We can study ensembles of long simulations in order to observe more averaged 
-  structure and to create more experimentally consistent XRD patterns. Extremely long simulations 
-  (on the order of \SI{}{\micro s}) may be necessary to better 
-  quantify the time scales for large scale rearrangements, and the precise arrangements themselves.
+  Future work, based on what has been learned in this study, may help further
+  improve the structural agreement between experiment and simulation. Force 
+  fields explicitly including $\pi-\pi$ interactions may be able to draw stacked
+  monomers closer together. We can study ensembles of long simulations in order
+  to observe more averaged structure and to create more experimentally consistent
+  XRD patterns. Extremely long simulations (on the order of \SI{}{\micro s}) may
+  be necessary to better quantify the time scales for large scale rearrangements,
+  and the precise arrangements themselves.
 

### 2018-09-15 Ben_Manuscripts/structure_paper/supporting_information.tex
revisions

@@
 
-\externaldocument[M-]{draft}
+\externaldocument[M-]{Draft}
 \title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
@@
   \begin{enumerate}
+
 	\item \textit{Create monomer structure file with connectivity} : We
@@
 	17.13~\cite{chemaxon_marvinsketch_2017} with all hydrogen atoms drawn out
-	explicitly. We optimized the 3D geometry of the structure using the 'Clean in
+	explicitly. We optimized the 3D geometry of the structure using the `Clean in
 	3D' function of MarvinSketch.  We saved the structure as a .mol file, then
@@
 	\cite{oboyle_open_2011,noauthor_open_nodate}.
+
 	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using
@@
 	tutorial can be accessed elsewhere \cite{walker_antechamber_nodate}.
+
 	\item \textit{Create GROMACS topologies from Amber output} : The output
@@
 	\texttt{LEaP} output into GROMACS .gro and .top files.
+
 	\item \textit{Perform a simulated annealing procedure on the monomer} :
@@
 	configuration from the last 10 \% of the trajectory.
+
 	\item \textit{Reassign charges with \texttt{molcharge}}: With the monomer
@@
 	new charges calculated by \texttt{molcharge}.
+
 	\item \textit{Anneal again to get final structure} : We repeated the
@@
 	(Figure~\ref{fig:monomer}).
+
   \end{enumerate} 
@@
 
-  We use the nematic order parameter as defined in section~\ref{method:nematic_order} to 
+  We use the nematic order parameter as defined in Section~\ref{method:nematic_order} to 
   observe any progress towards system ordering. In both cases, we see that the nematic
@@
   \end{figure}
+
+  \section{Number of monomers per column}\label{section:monomers_per_column}
+
+  We chose to build all systems using 20 monomers per column. We made this choice
+  by considering a number of factors that directly affect the quality of our results. 
+  Clearly, choosing a small number of layers will cause the system to suffer from 
+  finite size effects. Even in our 20 monomer-per-column system, axial correlations
+  between stacked monomers persist throughout the entire correlation function (see
+  Figure~\ref{M-fig:correlation} of the main text). The correlation function of the system which we
+  built with 40 monomers per column is very similar to that created with 20 monomers
+  per columns (continues to oscillate for its full length
+  (Figure~\ref{fig:tall_correlation_full})). If we continue adding monomers, the 
+  correlation function will eventually fully decay but it is not worth the 
+  computational expense. Regardless, the correlation lengths calculated from 20
+  monomer per column simulations are in sufficient agreement with experiment.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{z_correlation_overlay.png}
+  \caption{}\label{fig:z_correlation_overlay}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{tall_correlation_full.png}
+  \caption{}\label{fig:tall_correlation_full}
+  \end{subfigure}
+  \caption{(a) The correlation functions generated from ordered basin sandwiched 
+  configurations are nearly the same when the $z$-dimension of the system is doubled.
+  (b) Oscillations persist throughout the length of the correlation function for the
+  sandwiched system in the ordered basin built with 40 monomers per column. The full
+  system is ca. 17 nm tall so the full correlation function covers half this length
+  since periodicity forces the remaining length to be its mirror image.}\label{fig:correlation_functions}
+  \end{figure}
+
+  We may be able to simulate systems using less than 20 monomers per column, but chose
+  to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
+  patterns. The size of the Fourier space bin in each dimension is determined by 
+  $\dfrac{2\pi}{L}$ where L is the length of a given box vector. The $z$-box vector 
+  for 20 monomer-per-column systems is $\approx$ 85 \AA which means we will see 
+  a reciprocal space resolution of 0.074 \AA$^{-1}$ in the z direction. Further decreasing
+  the resolution would increase the noise in the simulated patterns and make it more
+  difficult to measure the intensity of reflections of interest.
 
@@
 	\begin{subfigure}{0.3\textwidth}
-		\includegraphics[width=\textwidth]{p2p_39.png}\quad
-		\vspace{-1.25em}
-		\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
-	\end{subfigure}
-	\begin{subfigure}{0.3\textwidth}
-		\includegraphics[width=\textwidth]{p2p_41.png}\quad
-		\vspace{-1.25em}
-		\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
-	\end{subfigure}
-	\begin{subfigure}{0.3\textwidth}
-		\includegraphics[width=\textwidth]{p2p_45.png}
-		\vspace{-1.25em}
-		\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
-	\end{subfigure}
-	\begin{subfigure}{0.3\textwidth}
-		\includegraphics[width=\textwidth]{p2p_50.png}\quad	
-		\vspace{-1.25em}
-		\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
-	\end{subfigure}
-	\begin{subfigure}{0.3\textwidth}
-		\includegraphics[width=\textwidth]{p2p_55.png}
-		\vspace{-1.25em}
-		\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
-	\end{subfigure}
-	\begin{subfigure}{0.3\textwidth}
 	\includegraphics[width=\textwidth]{p2p_diagram.png}
@@
   	\end{subfigure} 
-	\caption{The pore spacing during the restrained portion of the
-	dry equilibration procedure is shown. Every 50 ps (0.05 ns) we reduce the 
-	force constant on the position restraints according to the sequence: 1000000,
+	\begin{subfigure}{0.3\textwidth}
+		\includegraphics[width=\textwidth]{p2p_39.png}\quad
+		\vspace{-1.25em}
+		\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
+	\end{subfigure}
+	\begin{subfigure}{0.3\textwidth}
+		\includegraphics[width=\textwidth]{p2p_41.png}\quad
+		\vspace{-1.25em}
+		\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
+	\end{subfigure}
+	\begin{subfigure}{0.3\textwidth}
+		\includegraphics[width=\textwidth]{p2p_45.png}
+		\vspace{-1.25em}
+		\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
+	\end{subfigure}
+	\begin{subfigure}{0.3\textwidth}
+		\includegraphics[width=\textwidth]{p2p_50.png}\quad	
+		\vspace{-1.25em}
+		\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
+	\end{subfigure}
+	\begin{subfigure}{0.3\textwidth}
+		\includegraphics[width=\textwidth]{p2p_55.png}
+		\vspace{-1.25em}
+		\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
+	\end{subfigure}
+	\caption{(a) In a perfect hexagonal, there are 5 distances that should be exactly
+	equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
+	are the same. All plots in (b)--(f) are the average of these distances and represent
+	the pore spacing during the restrained portion of the dry equilibration procedure.
+	Every 50 ps (0.05 ns) we reduce the force constant on the position restraints according to the sequence: 1000000,
 	3162, 56, 8, 3, 2, 1, 0 kJ mol$^{-1}$ nm$^{-2}$. When we chose an initial pore
-	spacing below experimental value (a) or at the experimental value (b), there
+	spacing below experimental value (b) or at the experimental value (c), there
 	is an abrupt change in pore spacing when the position restraints are reduced to 56 kJ
-	mol$^{-1}$ nm$^{-2}$. When we initially position pores 45 \AA~apart (c) the pore spacing
-	remains relatively stable. When we initially place pores 50 \AA~apart (d), the pore
+	mol$^{-1}$ nm$^{-2}$. When we initially position pores 45 \AA~apart (d) the pore spacing
+	remains relatively stable. When we initially place pores 50 \AA~apart (e), the pore
 	spacing decreases nearly linearly once the restraints are reduced to 56 kJ
-	mol$^{-1}$ nm$^{-2}$. When we initially place pores 55 \AA~apart (e), so that monomers
+	mol$^{-1}$ nm$^{-2}$. When we initially place pores 55 \AA~apart (f), so that monomers
 	do not intersect with adjacent pores, and position restraints are reduced to 56
 	kJ mol$^{-1}$ nm$^{-2}$, the pore spacing changes erratically before stabilizing
-	when force constants are reduced below 3 kJ mol$^{-1}$ nm$^{-2}$. (f)
-	In a perfect hexagonal, there are 5 distances that should be exactly
-	equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
-	are the same. All plots in (a)--(e) are the average of these distances.} 
+	when force constants are reduced below 3 kJ mol$^{-1}$ nm$^{-2}$. } 
 	\label{fig:p2p}
@@
 
-  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.
-
-  \section{Number of monomers per column}\label{section:monomers_per_column}
-
-  We chose to build all systems using 20 monomers per column. We made this choice
-  by considering a number of factors that directly affect the quality of our results. 
-  Clearly, choosing a small number of layers will cause the system to suffer from 
-  finite size effects. Even in our 20 monomer-per-column system, axial correlations
-  between stacked monomers persist throughout the entire correlation function (see
-  Figure ~\ref{M-fig:correlation}). The correlation function of the system which we
-  built with 40 monomers per column is very similar to that created with 20 monomers
-  per columns (continues to oscillate for its full length
-  (Figure~\ref{fig:tall_correlation_full}). If we continue adding monomers, the 
-  correlation function will eventually fully decay but it is not worth the 
-  computational expense. Regardless, the correlation lengths calculated from 20
-  monomer per column simulations are in sufficient agreement with experiment.
+  Based on evidence from section~\ref{M-section:rpi} of the main text, we
+  believe it is most likely that the head groups stack somewhere between
+  the sandwiched and parallel displaced modes which we studied (Figure~\ref{fig:between_pd}).
 
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{z_correlation_overlay.png}
-  \caption{}\label{fig:z_correlation_overlay}
+  \centering
+  \includegraphics[width=\textwidth]{pd_36.eps}
+  \caption{}\label{fig:pd_36}
   \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{tall_correlation_full.png}
-  \caption{}\label{fig:tall_correlation_full}
-  \end{subfigure}
-  \caption{(a) The correlation functions generated from ordered basin sandwiched 
-  configurations are nearly the same when the $z$-dimension of the system is doubled.
-  (b) Oscillations persist throughout the length of the correlation function for the
-  sandwiched system in the ordered basin built with 40 monomers per column. The full
-  system is ca. 17 nm tall so the full correlation function covers half this length
-  since periodicity forces the remaining length to be its mirror image.}\label{fig:correlation_functions}
-  \end{figure}
-
-  We may be able to simulate systems using less than 20 monomers per column, but chose
-  to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
-  patterns. The size of the Fourier space bin in each dimension is determined by 
-  $\dfrac{2\pi}{L}$ where L is the length of a given box vector. The $z$-box vector 
-  for 20 monomer-per-column systems is $\approx$ 85 \AA which means we will see 
-  a reciprocal space resolution of 0.074 \AA$^{-1}$ in the z direction. Further decreasing
-  the resolution would increase the noise in the simulated patterns and make it more
-  difficult to measure the intensity of reflections of interest.
+  \centering
+  \includegraphics[width=\textwidth]{pd_lt36.eps}
+  \caption{}\label{fig:pd_lt36}
+  \end{subfigure}
+  \caption{Head groups are likely stacked in a configuration between sandwiched and
+  parallel displaced. (a) In our parallel displaced configurations with 5 columns 
+  per pore, we placed head groups so the angle, $\theta$, between vectors extending
+  from vertically stacked head groups to the pore center equals 36$\degree$ 
+  ((360$\degree$ / $ncol$) / 2 , where $ncol$ is the number of columns per pore). 
+  (b) In the true configuration, $\theta$ is likely distributed between 0$\degree$
+  and 36 $\degree$. When $\theta$=0$\degree$, the system architecture is the same
+  as a sandwiched configuration.}\label{fig:between_pd}
+  \end{figure}
 
@@
   \centering
-  \begin{tabular}{cc}
+  \begin{tabular}{ccc}
   \toprule
   System                         & Pore Spacing ($nm$) & Pore Spacing ($nm$)              \\
-                                 & Pore centers        & $\dfrac{x-box vector}{2}$ ($nm$) \\ 
+                                 & Pore centers        & $\dfrac{x\ box\ vector}{2}$ ($nm$) \\ 
   \midrule
@@
 
+  \section{Component radial density functions}\label{section:radial_density}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{offset_density.png}
+        \caption{Parallel Displaced, Ordered Pore Basin}
+        \label{fig:offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{layered_density.png}
+        \caption{Sandwiched, Ordered Pore Basin}
+        \label{fig:layered_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
+        \caption{Parallel Displaced, Disordered Pore Basin}
+        \label{fig:disordered_offset_density}
+  \end{subfigure}
+  \begin{subfigure}{0.47\textwidth}
+        \includegraphics[width=1\linewidth]{disordered_density.png}
+        \caption{Sandwiched, Disordered Pore Basin}
+        \label{fig:disorder_layered_density}
+  \end{subfigure}
+  %MRS8: at least one of these would be good to put in the main paper.
+  \caption{In all cases, the component radial distribution functions exhibit a
+	  composition gradient transitioning from the hydrophilic to the hydrophobic
+	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
+	  displaced (a), and sandwiched (b) configurations both show the highest
+	  concentrations of ions and head groups away from the pore center. Systems with
+	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
+	  concentrations of ions and head groups near the pore center, implying a more
+	  uniform, disordered pore.}~\label{fig:densities}
+  \end{figure}
+  \clearpage
+
+  \begin{figure}
+  \begin{minipage}{0.45\linewidth}
+  \centering
+  \includegraphics[width=\textwidth]{monomer_color_coded.png}
+  \vspace{4.5em}
+  \caption{The groups used for radial distribution calculations. Red atoms are in the
+  tails group. Green atoms are in the head group region. The blue atom is sodium.}\label{fig:monomer_color_coded}
+  \end{minipage}\qquad
+  \begin{minipage}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{radial_distribution_annulus.png}
+  \caption{
+  Looking down onto the plane of membrane, 
+  % this diagram
+  % illustrates how we calculated radial distribution
+  % functions.
+  we binned the radial distance of all atoms in chosen groups from
+  pore centers. The bins are defined by the annulus bounded by concentric
+  circles centered at the pore centers, as shown. We normalize by
+  dividing the count of atoms within each bin annulus by its volume.
+%  of
+%  the annulus where the volume is the area of the annulus times the
+%  height of the membrane in the z-direction.
+  }~\label{fig:rdf_diagram}
+  \end{minipage}
+  \end{figure}
+% BJC: Unnecessary, supporting info already long
+%  \begin{figure}
+%	\centering
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_layered_4.png}
+%                \caption{4 mon/layer, Sandwiched}\label{fig:zdf_layered_4}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_offset_4.png}
+%                \caption{4 mon/layer, Parallel Displaced}\label{fig:zdf_layered_4}
+%        \end{subfigure}
+%	\begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_layered_6.png}
+%                \caption{6 mon/layer, Sandwiched}\label{fig:zdf_layered_6}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_offset_6.png}
+%                \caption{6 mon/layer, Parallel Displaced}\label{fig:zdf_layered_6}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_layered_7.png}
+%                \caption{7 mon/layer, Sandwiched}\label{fig:zdf_layered_7}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_offset_7.png}
+%                \caption{7 mon/layer, Parallel Displaced}\label{fig:zdf_layered_7}
+%        \end{subfigure}
+%	\begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_layered_8.png}
+%                \caption{8 mon/layer, Sandwiched}\label{fig:zdf_layered_8}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{zdf_offset_8.png}
+%                \caption{8 mon/layer, Parallel Displaced}\label{fig:zdf_layered_8}
+%        \end{subfigure}
+%	\caption{$g(z)$ for all other configurations built with layers stacked 3.7 \AA~apart}\label{fig:zdf}
+%  \end{figure}
+
+%BJC: unnecessary. Supporting info already long..and more is coming
+%  \begin{figure}
+%	\centering
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_layered_4.png}
+%                \caption{4 mon/layer, Sandwiched}\label{fig:rzplot_layered_4}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_offset_4.png}
+%                \caption{4 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_4}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_layered_6.png}
+%                \caption{6 mon/layer, Sandwiched}\label{fig:rzplot_layered_6}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_offset_6.png}
+%                \caption{6 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_6}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_layered_7.png}
+%                \caption{7 mon/layer, Sandwiched}\label{fig:rzplot_layered_7}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_offset_7.png}
+%                \caption{7 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_7}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_layered_8.png}
+%                \caption{8 mon/layer, Sandwiched}\label{fig:rzplot_layered_8}
+%        \end{subfigure}
+%        \begin{subfigure}{0.40\textwidth}
+%                \centering
+%                \includegraphics[width=\textwidth]{rzplot_offset_8.png}
+%                \caption{8 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_8}
+%        \end{subfigure}
+%	\caption{Simulated XRD patterns for all other configurations built with
+%		 layers stacked 3.7 \AA~apart}\label{fig:XRDsim}
+%  \end{figure}
+
+%  \begin{wrapfigure}{R}{0.4\textwidth}
+%      \centering
+%      \includegraphics[width=0.4\textwidth]{tilt.png}
+%      \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}     
+%  \end{wrapfigure}
+
+%  \begin{figure}
+%	\centering
+%	\begin{subfigure}{0.45\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{ps5layered.png}
+%		\caption{}\label(fig:ps5layered}
+%	\end{subfigure}
+%	\begin{subfigure}
+%		\centering
+%		\includegraphics[width=\textwidth]{ps5offset.png}
+%		\caption{}\label{fig:ps5offset} 
+%	\end{subfigure}
+%  \end{figure}
+
+  \section{2D Small Angle X-ray Scattering Data}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{2DSAXS_axes.png}
+  \caption{Two dimensional small angle X-ray scattering experiments show
+  reflections along the $q_r$ axis at $q_z$=0. The spacing between the reflections
+  is characteristic of a hexagonal phase and is directly related to the distance
+  between pores. The reflections are arced because the pores are not perfectly
+  aligned. A perfectly aligned system would show dots at each peak location. An
+  isotropically aligned system would show concentric rings about the origin which
+  pass through each peak location. The d\textsubscript{100} and d\textsubscript{110} 
+  peaks (the first two pairs of reflections from origin located at $|\mathbf{q}| 
+  \approx 0.18~\AA^{-1}$ and $|\mathbf{q}| \approx 0.31~\AA^{-1}$) are not visible
+  in the 2D WAXS pattern. The edges of the d\textsubscript{200} reflection (the third
+  pair of reflections located at $|\mathbf{q}| \approx 0.36~\AA^{-1}$) are slightly
+  visible in the 2D WAXS pattern, so we used them to approximate the experimental
+  intensity of R-pores.}\label{fig:2DSAXS}
+  \end{figure}
+
+  \section{Ionic Conductivity}\label{section:ionic_conductivity}
+
+  In the main text, we calculated ionic conductivity using the Nernst-Einstein 
+  relationship. We also measured ionic conductivity using a second method, 
+  termed the Collective Diffusion model, for robustness. The collective 
+  diffusion model measures the movement of the collective variable, Q, which
+  is defined as the amount of charge transfer through the system and can be 
+  thought to represent the center of charge of the system. The conductance, 
+  $\gamma$, of the system can be calculated as:
+  \begin{equation}
+	 \gamma = \dfrac{D_Q}{k_b T} 
+	\label{eqn:collective_diffusion}
+  \end{equation}
+  $D_Q$ is the diffusion coefficient of the collective variable Q and is 
+  calculated using the Einstein relation. We convert the resulting value
+  to ionic conductivity by multiplying by channel length and dividing by
+  the membrane cross sectional area. One can access a detailed derivation of 
+  the model elsewhere\cite{liu_collective_2013}.
+
+  \begin{figure}[!htb]
+        \centering
+        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
+        \caption{The Collective Diffusion model and the Nernst-Einstein relation yield
+        agreeing values of ionic conductivity for both types of ordered basin systems 
+        simulated. Both methods estimate the value of the ionic conductivity to be an 
+        order of magnitude higher than the experimental value. There is more noise in
+        the collective diffusion model because there is inherently less data that 
+        can be used for its calculation. For that reason, we use only the Nernst-Einstein relationship in the main text.}
+        \label{fig:conductivity}
+  \end{figure}
+
+  \section{Crosslinking algorithm details}\label{section:xlink}
+
+  Crosslinking of the the monomer Na-GA3C11 occurs via a UV initiated free
+  radical polymerization (FRP) (Figure~\ref{fig:xlink_mech}). Head-to-tail addition
+  takes place between terminal vinyl groups on each of the monomer tails. We
+  only considered head-to-tail addition since it is the dominant propagation mode
+  in the real system.
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=\textwidth]{Crosslink_mechanism.eps}
+  \caption{Terminal vinyl groups present on each monomer tail react with free
+	  radical initiators to create monomers with terminal vinyl radicals.  Vinyl
+	  radicals react with the vinyl groups of other monomers in order to propagate
+	  crosslinking.}\label{fig:xlink_mech}
+  \end{figure}
+
+  We based our cross-linking algorithm on the known reaction mechanism.
+  FRPs require an initiator which bonds to the system, meaning new atoms are
+  introduced into the system. For simplicity, we simulated the initiator as
+  hydrogen and made it present in the simulation by including them as dummy atoms
+  in all possible locations where an addition could occur. We carry out the
+  cross-linking procedure iteratively. During each iteration, the algorithm
+  selects eligible bonding carbon atoms based on a distance cut-off. The algorithm
+  then updates the topology with new bonds and changes dummy hydrogen atoms to appropriate
+  hydrogen atom types. We only considered head-to-tail addition
+  due to its dominance in the real system \cite{young_introduction_2011}. We did
+  not consider direction of attack because the resultant mixture is racemic.
+
+  Our implementation requires long simulation times to achieve high cross-link 
+  densities. A typical cross-linking procedure can take up to 24 hours. In
+  order to collect equilibrated data, further NPT simulation is necessary. We
+  typically run a cross-linked system for an additional 100 ns to allow the system
+  to readjust. For those reasons we did not cross-link all systems tested.
+
+  \clearpage
   \section{The nematic order parameter}\label{method:nematic_order}
@@
   $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
-  order parameter, $S$, is defined as:
+  order parameter, $S$, is defined as:~\cite{chaikin_principles_1995}
   \begin{equation}
@@
   We are interested in quantifying the degree of monomer head group alignment 
-  between systems. We use Eq.~\ref{eqn:nematic_order_parameter} to accomplish this
-  by defining $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
+  between systems. We use Equation~\ref{eqn:nematic_order_parameter} to accomplish this
+  by defining $\mathbf{n}$ as the $z$-axis (or pore axis), and then measuring the angles,
   $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
@@
   \caption{We calculate the nematic order parameter by measuring the angle
-  between $\mathbf{v}$ and the z-axis.}~\label{fig:director}
+  between $\mathbf{v}$ and the $z$-axis.}~\label{fig:director}
   \end{figure}
@@
   \caption{The distribution of angles between nematic director vector (see
-	  Figure~\ref{fig:director}) and the z-axis averaged over the equilibrated portion
-	  of each trajectory}~\label{fig:nematic_distribution}
+	  Figure~\ref{fig:director}) and the $z$-axis averaged over the equilibrated portion
+	  of each trajectory. The ordered sandwiched configuration has a higher nematic order
+	  parameter than the ordered parallel displaced configuration. The disordered
+	  sandwiched configuration has a higher nematic order parameter than the 
+	  disordered parallel displaced configuration.}~\label{fig:nematic_distribution}
   \end{figure}
@@
 
-  \section{Component radial density functions}\label{section:radial_density}
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{offset_density.png}
-        \caption{Parallel Displaced, Ordered Pore Basin}
-        \label{fig:offset_density}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{layered_density.png}
-        \caption{Sandwiched, Ordered Pore Basin}
-        \label{fig:layered_density}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
-        \caption{Parallel Displaced, Disordered Pore Basin}
-        \label{fig:disordered_offset_density}
-  \end{subfigure}
-  \begin{subfigure}{0.47\textwidth}
-        \includegraphics[width=1\linewidth]{disordered_density.png}
-        \caption{Sandwiched, Disordered Pore Basin}
-        \label{fig:disorder_layered_density}
-  \end{subfigure}
-  %MRS8: at least one of these would be good to put in the main paper.
-  \caption{In all cases, the component radial distribution functions exhibit a
-	  composition gradient transitioning from the hydrophilic to the hydrophobic
-	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
-	  displaced (a), and sandwiched (b) configurations both show the highest
-	  concentrations of ions and head groups away from the pore center. Systems with
-	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
-	  concentrations of ions and head groups near the pore center, implying a more
-	  uniform, disordered pore.}~\label{fig:densities}
-  \end{figure}
-  \clearpage
-
-  \begin{figure}
-  \begin{minipage}{0.45\linewidth}
-  \centering
-  \includegraphics[width=\textwidth]{monomer_color_coded.png}
-  \vspace{4.5em}
-  \caption{The groups used for radial distribution calculations. Red atoms are in the
-  tails group. Green atoms are in the head group region. The blue atom is sodium.}\label{fig:monomer_color_coded}
-  \end{minipage}\qquad
-  \begin{minipage}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{radial_distribution_annulus.png}
-  \caption{
-  Looking down onto the plane of membrane, 
-  % this diagram
-  % illustrates how we calculated radial distribution
-  % functions.
-  we binned the radial distance of all atoms in chosen groups from
-  pore centers. The bins are defined by the annulus bounded by concentric
-  circles centered at the pore centers, as shown. We normalize by
-  dividing the count of atoms within each bin annulus by its volume.
-%  of
-%  the annulus where the volume is the area of the annulus times the
-%  height of the membrane in the z-direction.
-  }~\label{fig:rdf_diagram}
-  \end{minipage}
-  \end{figure}
-% BJC: Unnecessary, supporting info already long
-%  \begin{figure}
-%	\centering
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_layered_4.png}
-%                \caption{4 mon/layer, Sandwiched}\label{fig:zdf_layered_4}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_offset_4.png}
-%                \caption{4 mon/layer, Parallel Displaced}\label{fig:zdf_layered_4}
-%        \end{subfigure}
-%	\begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_layered_6.png}
-%                \caption{6 mon/layer, Sandwiched}\label{fig:zdf_layered_6}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_offset_6.png}
-%                \caption{6 mon/layer, Parallel Displaced}\label{fig:zdf_layered_6}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_layered_7.png}
-%                \caption{7 mon/layer, Sandwiched}\label{fig:zdf_layered_7}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_offset_7.png}
-%                \caption{7 mon/layer, Parallel Displaced}\label{fig:zdf_layered_7}
-%        \end{subfigure}
-%	\begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_layered_8.png}
-%                \caption{8 mon/layer, Sandwiched}\label{fig:zdf_layered_8}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{zdf_offset_8.png}
-%                \caption{8 mon/layer, Parallel Displaced}\label{fig:zdf_layered_8}
-%        \end{subfigure}
-%	\caption{$g(z)$ for all other configurations built with layers stacked 3.7 \AA~apart}\label{fig:zdf}
-%  \end{figure}
-
-%BJC: unnecessary. Supporting info already long..and more is coming
-%  \begin{figure}
-%	\centering
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{rzplot_layered_4.png}
-%                \caption{4 mon/layer, Sandwiched}\label{fig:rzplot_layered_4}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{rzplot_offset_4.png}
-%                \caption{4 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_4}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{rzplot_layered_6.png}
-%                \caption{6 mon/layer, Sandwiched}\label{fig:rzplot_layered_6}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{rzplot_offset_6.png}
-%                \caption{6 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_6}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{rzplot_layered_7.png}
-%                \caption{7 mon/layer, Sandwiched}\label{fig:rzplot_layered_7}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{rzplot_offset_7.png}
-%                \caption{7 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_7}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{rzplot_layered_8.png}
-%                \caption{8 mon/layer, Sandwiched}\label{fig:rzplot_layered_8}
-%        \end{subfigure}
-%        \begin{subfigure}{0.40\textwidth}
-%                \centering
-%                \includegraphics[width=\textwidth]{rzplot_offset_8.png}
-%                \caption{8 mon/layer, Parallel Displaced}\label{fig:rzplot_offset_8}
-%        \end{subfigure}
-%	\caption{Simulated XRD patterns for all other configurations built with
-%		 layers stacked 3.7 \AA~apart}\label{fig:XRDsim}
-%  \end{figure}
-
-%  \begin{wrapfigure}{R}{0.4\textwidth}
-%      \centering
-%      \includegraphics[width=0.4\textwidth]{tilt.png}
-%      \caption{The average angle between alkane chains and the xy plane is nearly zero degrees}\label{fig:tilt}     
-%  \end{wrapfigure}
-
-%  \begin{figure}
-%	\centering
-%	\begin{subfigure}{0.45\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{ps5layered.png}
-%		\caption{}\label(fig:ps5layered}
-%	\end{subfigure}
-%	\begin{subfigure}
-%		\centering
-%		\includegraphics[width=\textwidth]{ps5offset.png}
-%		\caption{}\label{fig:ps5offset}
-%	\end{subfigure}
-%  \end{figure}
-  \section{Tail organization}
+  \section{The effect of imposed tail tilt}\label{section:tail_tilt}
+
+  Monomer tails prefer to lie flat rather than tilt with respect to the
+  membrane plane. We created a monomer whose tails tilted ca. 30$\degree$. 
+  We added position restraints to the ends of the monomer tails with the
+  same force constant as the head groups (see section~\ref{section:equilibration}).
+  As we slowly reduce the force constants, the tails begin to tend towards
+  a negligible tilt angle (Figure~\ref{fig:tail_tilt}).
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{tilt_cat.png}
+  \caption{As we reduce the force constants applied to the end of each
+  tail of an initially tilted monomer configuration, the average tilt 
+  angle with respect to the membrane plane decreases until it is nearly
+  negligible.}\label{fig:tail_tilt}
+  \end{figure}
+
+  \section{Tail organization}\label{section:tail_packing}
 
   In order to understand the origin of R-spots, we looked for ordering among
-  the tails. We divided the tail into three sections: tail fronts, tail 
-  middles and tail ends. The sections are illustrated in 
-  Figure~\ref{fig:tail_sections}.
+  the tails. We divided the tail into three sections: tail-fronts, tail-middles
+  and tail-ends. The sections are illustrated in Figure~\ref{fig:tail_sections}.
 
@@
   \caption{We divided the tail into three regions: tail-fronts (blue), 
-  tail-middles (green) and tail-backs (red).}\label{fig:tail_sections}
+  tail-middles (green) and tail-ends (red).}\label{fig:tail_sections}
   \end{figure}
@@
   same tail section. For example, Figure~\ref{fig:centroids} shows a 3D plot of
-  the center of masses of each tail front. We wanted to know average location
+  the center of masses of each tail front. We wanted to know the average location
   of nearest neighbors to each center of mass. The red bead in 
@@
 
-  \section{Diffusion of monomers}
-
-  We calculated the diffusion coefficient of the monomer head groups by measuring
-  the slope of the linear region of their mean squared displacement curves accumulated
-  over the length of the equilibration simulations (Table~\ref{table:msd}).
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{cc}
-  \toprule
-  System & Diffusion Constant ($m^2/s$) \\ 
-  \midrule
-  Sandwiched, Ordered & $1.4 \times 10^{-14}$ \\
-  Parallel Displaced, Ordered & $2.0 \times 10^{-14}$ \\
-  Sandwiched, Disordered & $2.0 \times 10^{-14}$ \\
-  Parallel Displaced, Disordered & $3.5 \times 10^{-14}$ \\
-  \bottomrule
-  \end{tabular}
-  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
-  .}~\label{table:msd}
-  \end{table}
+  \section{Carboxylate Dihedrals}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{carboxylate_dihedral_rb.png}
+  \caption{A potential energy diagram for the dihedral angle about the carbon-carbon bond of
+  a carboxylate group attached to an aromatic ring, using parameters from the generalized amber 
+  forcefield. It is energetically favorable for the carboxylate group to stay in plane with 
+  the aromatic ring. There is a large energy penalty as the dihedral becomes antiparallel to 
+  the plane of the aromatic ring.}\label{fig:carboxylate_dihedral_rb}
+  \end{figure}
 
@@
 
-  \section{Crosslinking algorithm details}\label{section:xlink}
-
-  Crosslinking of the the monomer Na-GA3C11 occurs via a UV initiated free
-  radical polymerization (FRP) (Figure~\ref{fig:xlink_mech}). Head-to-tail addition
-  takes place between terminal vinyl groups on each of the monomer tails. We
-  only considered head-to-tail addition since it is the dominant propagation mode
-  in the real system.
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=\textwidth]{Crosslink_mechanism.eps}
-  \caption{Terminal vinyl groups present on each monomer tail react with free
-	  radical initiators to create monomers with terminal vinyl radicals.  Vinyl
-	  radicals react with the vinyl groups of other monomers in order to propagate
-	  crosslinking.}\label{fig:xlink_mech}
-  \end{figure}
-
-  We based our cross-linking algorithm on the known reaction mechanism.
-  FRPs require an initiator which bonds to the system, meaning new atoms are
-  introduced into the system. For simplicity, we simulated the initiator as
-  hydrogen and made it present in the simulation by including them as dummy atoms
-  in all possible locations where an addition could occur. We carry out the
-  cross-linking procedure iteratively. During each iteration, the algorithm
-  selects eligible bonding carbon atoms based on a distance cut-off. The algorithm
-  then updates the topology with new bonds and changes dummy hydrogen atoms to appropriate
-  hydrogen atom types. We only considered head-to-tail addition
-  due to its dominance in the real system \cite{young_introduction_2011}. We did
-  not consider direction of attack because the resultant mixture is racemic.
-
-  Our implementation requires long simulation times to achieve high cross-link 
-  densities. A typical cross-linking procedure can take up to 24 hours. In
-  order to collect equilibrated data, further NPT simulation is necessary. We
-  typically run a cross-linked system for an additional 100 ns to allow the system
-  to readjust. For those reasons we did not cross-link all systems tested.
-
-  \clearpage
-
-  \section{Ionic Conductivity}\label{section:ionic_conductivity}
-
-  In the main text, we calculated ionic conductivity using the Nernst-Einstein 
-  relationship. We also measured ionic conductivity using a second method, 
-  termed the Collective Diffusion model, for robustness. The collective 
-  diffusion model measures the movement of the collective variable, Q, which
-  is defined as the amount of charge transfer through the system and can be 
-  thought to represent the center of charge of the system. The conductance, 
-  $\gamma$, of the system can be calculated as:
-  \begin{equation}
-	 \gamma = \dfrac{D_Q}{k_b T} 
-	\label{eqn:collective_diffusion}
-  \end{equation}
-  $D_Q$ is the diffusion coefficient of the collective variable Q and is 
-  calculated using the Einstein relation. We convert the resulting value
-  to ionic conductivity by multiplying by channel length and dividing by
-  the membrane cross sectional area. One can access a detailed derivation of 
-  the model elsewhere\cite{liu_collective_2013}.
-
-  \begin{figure}[!htb]
-        \centering
-        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
-        \caption{The Collective Diffusion model and the Nernst-Einstein relation yield
-        agreeing values of ionic conductivity for both types of ordered basin systems 
-        simulated. Both methods estimate the value of the ionic conductivity to be an 
-        order of magnitude higher than the experimental value. There is more noise in
-        the collective diffusion model because there is inherently less data that 
-        can be used for its calculation. For that reason, we use only the Nernst-Einstein relationship in the main text.}
-        \label{fig:conductivity}
-  \end{figure}
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=0.5\textwidth]{carboxylate_dihedral_rb.png}
-  \caption{A potential energy diagram for the dihedral angle about the carbon-carbon bond of
-  a carboxylate group attached to an aromatic ring, using parameters from the generalized amber 
-  forcefield. It is energetically favorable for the carboxylate group to stay in plane with 
-  the aromatic ring. There is a large energy penalty as the dihedral becomes antiparallel to 
-  the plane of the aromatic ring.}\label{fig:carboxylate_dihedral_rb}
-  \end{figure}
-
-%  \begin{figure}[!htb]
-%  \centering
-%  \begin{subfigure}{width=0.45\textwidth}
-%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
-%  \caption{}\label{fig:rdouble_offset_solvated_rzplot}
-%  \end{subfigure}
-%  \begin{subfigure}{width=0.45\textwidth}
-%  \includegraphics[width=\textwidth]{rzplot_pore1_removed.png}
-%  \caption{}\label{fig:rzplot_pore1_removed}
-%  \end{subfigure}
-%  \caption{(a) The simulated diffraction pattern of a system simulated in an ordered basin 
-%  parallel displaced configuration with 1 wt\% water shows R-double at $mathbf{q}=(0, 0.7) \AA^{-1}$.
-%  (b) When we remove }\label{fig:pore1_removed}
-%  \end{figure}
+  \section{Diffusion of monomers}
+
+  We calculated the diffusion coefficient of the monomer head groups by measuring
+  the slope of the linear region of their mean squared displacement curves accumulated
+  over the length of the equilibration simulations (Table~\ref{table:msd}).
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cc}
+  \toprule
+  System & Diffusion Constant ($m^2/s$) \\ 
+  \midrule
+  Sandwiched, Ordered & $1.4 \times 10^{-14}$ \\
+  Parallel Displaced, Ordered & $2.0 \times 10^{-14}$ \\
+  Sandwiched, Disordered & $2.0 \times 10^{-14}$ \\
+  Parallel Displaced, Disordered & $3.5 \times 10^{-14}$ \\
+  \bottomrule
+  \end{tabular}
+  \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
+  .}~\label{table:msd}
+  \end{table}
+
+  \section{Autocorrelation of monomer dihedrals}
+
+  In section~\ref{M-section:slow_dynamics} of the main text, we calculated the
+  autocorrelation function of the outer tail either dihedrals pictured
+  in Figure~\ref{fig:dihedrals}.
 
@@
 
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=0.5\textwidth]{2DSAXS_axes.png}
-  \caption{Two dimensional small angle X-ray scattering experiments show
-  reflections along the $q_r$ axis at $q_z$=0. The spacing between the reflections
-  is characteristic of a hexagonal phase and is directly related to the distance
-  between pores. The reflections are arced because the pores are not perfectly
-  aligned. A perfectly aligned system would show dots at each peak location. An
-  isotropically aligned system would show concentric rings about the origin which
-  pass through each peak location. The d\textsubscript{100} and d\textsubscript{110} 
-  peaks (the first two pairs of reflections from origin located at $|\mathbf{q}| 
-  \approx 0.18~\AA^{-1}$ and $|\mathbf{q}| \approx 0.31~\AA^{-1}$) are not visible
-  in the 2D WAXS pattern. The edges of the d\textsubscript{200} reflection (the third
-  pair of reflections located at $|\mathbf{q}| \approx 0.36~\AA^{-1}$) are slightly
-  visible in the 2D WAXS pattern, so we used them to approximate the experimental
-  intensity of R-pores.}\label{fig:2DSAXS}
-  \end{figure}
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{width=0.45\textwidth}
+%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
+%  \caption{}\label{fig:rdouble_offset_solvated_rzplot}
+%  \end{subfigure}
+%  \begin{subfigure}{width=0.45\textwidth}
+%  \includegraphics[width=\textwidth]{rzplot_pore1_removed.png}
+%  \caption{}\label{fig:rzplot_pore1_removed}
+%  \end{subfigure}
+%  \caption{(a) The simulated diffraction pattern of a system simulated in an ordered basin 
+%  parallel displaced configuration with 1 wt\% water shows R-double at $mathbf{q}=(0, 0.7) \AA^{-1}$.
+%  (b) When we remove }\label{fig:pore1_removed}
+%  \end{figure}
 

### 2018-09-17 Ben_Manuscripts/structure_paper/Draft.tex
Converting to pdfs

@@
 \affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
-\author{Richard D. Noble}
+%\author{Richard D. Noble}
 \author{Douglas L. Gin}
@@
 		\centering
-		\includegraphics[width=\textwidth]{monomer_twocolor.png}
+		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
 		\caption{}~\label{fig:atomistic_monomer}
@@
 		\centering
-		\includegraphics[width=\textwidth]{wedge_thick.png}
+		\includegraphics[width=\textwidth]{wedge_thick.pdf}
 		\caption{}~\label{fig:wedge}
@@
 		\centering
-		\includegraphics[width=\textwidth]{columns.png}
+		\includegraphics[width=\textwidth]{columns.pdf}
 		\caption{}~\label{fig:wedge_layer}
@@
 		\centering
-		\includegraphics[width=\textwidth]{hexagonal_packing.png}
+		\includegraphics[width=\textwidth]{hexagonal_packing.pdf}
 		\caption{}~\label{fig:hex_packing_simple}
@@
 		\centering
-		\includegraphics[width=\textwidth]{cartoon_pore.png}
+		\includegraphics[width=\textwidth]{cartoon_pore.pdf}
 		\caption{}~\label{fig:undetailed_pore}
@@
 		\centering
-		\includegraphics[width=\textwidth]{detailed_pore.png}
+		\includegraphics[width=\textwidth]{detailed_pore.pdf}
 		\caption{}~\label{fig:detailed_pore}
@@
                 \centering
-                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
+                \includegraphics[width=\linewidth]{WAXS_annotated_words.pdf} 
                 \caption{}\label{fig:WAXS}
@@
                 \centering
-                \includegraphics[width=\linewidth]{SAXS.png}
+                \includegraphics[width=\textwidth]{SAXS.pdf}
                 \caption{}\label{fig:SAXS}
@@
   \begin{subfigure}[t]{0.45\textwidth}
-  \includegraphics[width=\linewidth]{monomer_diagonal.png}
+  \includegraphics[width=\linewidth]{monomer_diagonal.pdf}
   \caption{}
@@
   \begin{subfigure}[t]{0.42\textwidth}
-  \includegraphics[width=\linewidth]{stacked_monomers.png}
+  \includegraphics[width=\linewidth]{stacked_monomers.pdf}
   \caption{}
@@
   \begin{subfigure}[t]{0.35\textwidth}
-  \includegraphics[width=\linewidth]{initial_pore.png}
+  \includegraphics[width=\linewidth]{initial_pore.pdf}
   \caption{}
@@
   \begin{subfigure}[t]{0.45\textwidth}
-  \includegraphics[width=\linewidth]{initial_unit_cell.png}
+  \includegraphics[width=\linewidth]{initial_unit_cell.pdf}
   \caption{}
@@
   \centering
-  \includegraphics[width=\textwidth]{ralkanes.png}
+  \includegraphics[width=\textwidth]{ralkanes.pdf}  % Search WAXS.py for: fancy demo of r-alkanes normalization
   \caption{R-alkanes}\label{fig:ralkanes}
@@
   \centering
-  \includegraphics[width=\textwidth]{rpi_rdouble.png}
+  \includegraphics[width=\textwidth]{rpi_rdouble.pdf}  %  Search WAXS.py for: R-pi / R-double intensity measurement illustration
   \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
@@
   \centering
-  \includegraphics[width=\textwidth]{angular_integration.png}
+  \includegraphics[width=\textwidth]{angular_integration.pdf} % Search WAXS.py for: Plot R-spots integrated intensity curve
   \caption{R-spots}\label{fig:rspots}
@@
   \centering
-  \includegraphics[width=\textwidth]{saxs_xsection.png}
+  \includegraphics[width=\textwidth]{saxs_xsection.pdf}  % 2DSAXS.py in Scripts folder 
   \caption{R-pores}\label{fig:saxs_xsection}
@@
 	\centering
-	\includegraphics[width=\linewidth]{p2p.png}
+	\includegraphics[width=\linewidth]{p2p.pdf}
 	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
@@
 			\centering
-		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
+		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.pdf}
 			\end{subfigure}
@@
 		       		\centering
-	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
+	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.pdf}
 			\end{subfigure}
@@
 		       		\centering
-	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
+	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.pdf}
 			\end{subfigure}
@@
 			\centering
-		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
+		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.pdf}
 			\end{subfigure}
@@
 				\centering
-			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
+			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.pdf}
 			\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{colorbar_jet.png}
+		\includegraphics[width=\linewidth]{colorbar_jet.pdf}
 	\end{subfigure}	
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
+  \includegraphics[width=\textwidth]{exp_rsection_fit.pdf}
   \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
+  \includegraphics[width=\textwidth]{exp_zsection_fit.pdf}
   \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
@@
   \begin{subfigure}{\textwidth}
-  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
+  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.pdf}
   \caption{}\label{fig:offset_ensemble_regional_density}

### 2018-09-18 Ben_Manuscripts/structure_paper/Draft.tex
Converted figures to .pdf

@@
 	  the locations of the reflections, R-pores, R-alkanes and R-spots appear at $q$
-	  values that close to experiemnt, while R-$\pi$ appears at a significantly lower
-	  $q$ value than experiment.}
-  \label{table:relative_intensities_300K} 
+	  values that close to experiment, while R-$\pi$ appears at a significantly lower
+	  $q$ value than experiment.\label{table:relative_intensities_300K}}
   \end{table}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.png}
+  	\includegraphics[width=\textwidth]{rzplot_layered_280K_jet.pdf}
   	\caption{}\label{fig:sandwiched280K}
@@
   \begin{subfigure}{0.32\linewidth}
-    \includegraphics[width=\textwidth]{tilt_dist.png}
+    \includegraphics[width=\textwidth]{tilt_dist.pdf}
     \caption{}\label{fig:tilt}
@@
 	\centering
-	\includegraphics[width=\textwidth]{tails_rzplot_jet.png}
+	\includegraphics[width=\textwidth]{tails_rzplot_jet.pdf}
 	\caption{}\label{fig:tails_rzplot}
@@
     \centering
-	\includegraphics[scale=0.2]{centroids.png}
+	\includegraphics[scale=0.2]{centroids.pdf}
   \caption{}\label{fig:centroids}
@@
         \centering
-	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.png}
+	        \includegraphics[width=\linewidth]{hexagonal_tail_packing.pdf}
 	        \caption{}~\label{fig:layered_tails}
@@
         	\centering
-	        \includegraphics[width=\linewidth]{hexagonal_ft.png}  % generated from hexagonal_packing.py
+	        \includegraphics[width=\linewidth]{hexagonal_ft.pdf}  % generated from hexagonal_packing.py
 	        \caption{}~\label{fig:hexagonal_ft}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
+  \includegraphics[width=\textwidth]{sim_rsection_fit.pdf}
   \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
+  \includegraphics[width=\textwidth]{sim_zsection_fit.pdf}
   \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
@@
   \centering
-  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
+  \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
   \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
@@
   \centering
-  \includegraphics[width=\textwidth]{z_correlation_offset.png}
+  \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
   \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
@@
   \centering
-  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
+  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
   \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
@@
   \centering
-  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
+  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
   \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
   \end{subfigure}  
-  %MRS10: should say something here about whether this is consistent or not with experiement (and why/why not)
-  %MRS10: maybe include correlation lengths as well calculated from these, and compare to experiment?
-I know it's in the table as well, but seems missing here.
-1D correlation functions are given, but not how that data proves central points.
   \caption{1D correlation functions of the center of masses of aromatic head
@@
   \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
+  \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
   \caption{}\label{fig:intensity_vs_zsigma}
@@
   \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
+  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
   \caption{}\label{fig:rpi_xsection_vs_zsigma}
@@
   systems.
-  %MRS12: somewhere will have to talk about stability and relative free energy of the more disordered initial configurations.
-  %MRS12: we MIGHT have to look at more disordered initial configurations.
-I think this can likely be done with just equilibration, where we see how different the quenched disorder when starting from an ensemble of structures, and putting off actually calculating scattring from a large number of simulations.
+
+  % produce figures with: structure_factor.py --random_columns -nframes 1000 --hexagonal -g 86 86 256 -thermal_disorder 2.30 0.43 1.48 -dbwl 4.4 --pore_radius 6.6 -box 85 85 352 -sr 0
+  % Adjust sr from 0 to .75 to 1
   \begin{figure}
@@
   \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qy_sr0.png}
+  \includegraphics[width=\textwidth]{sf_qy_sr0.pdf}
   \caption{$f$ = 0}\label{fig:sf_qy_sr0}
@@
   \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qy_sr75.png}
+  \includegraphics[width=\textwidth]{sf_qy_sr75.pdf}
   \caption{$f$ = 0.75}\label{fig:sf_qy_sr75}
@@
   \begin{subfigure}{0.3\textwidth}
-  \includegraphics[width=\textwidth]{sf_qy_sr100.png}
+  \includegraphics[width=\textwidth]{sf_qy_sr100.pdf}
   \caption{$f$ = 1}\label{fig:sf_qy_sr100}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.png}
+  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.pdf}
   \caption{When we average all $z$-slices of the 3D correlation function, the 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
+  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
   \caption{Increasing the amount of disorder in the $xy$ plane decreases the
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.png}
+  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.pdf}
   \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{offset_ensemble_rsection.png}
+  \includegraphics[width=\textwidth]{offset_ensemble_rsection.pdf}
   \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
@@
   \begin{subfigure}{\textwidth}
-  \includegraphics[width=\textwidth]{offset_ensemble_pooled.png}
+  \includegraphics[width=\textwidth]{offset_ensemble_pooled.pdf}
   \caption{Distributions of deviations from ideal positions generated with data
@@
   %MRS15: 95% is fine.
-  \includegraphics[width=\textwidth]{offset_ecdfs.png}
+  \includegraphics[width=\textwidth]{offset_ecdfs.pdf}
   \caption{Empirical cumulative distribution functions generated from (a) and
@@
   \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{offset_ensemble_stds.png}
+  \includegraphics[width=\textwidth]{offset_ensemble_stds.pdf}
   \caption{}\label{fig:offset_ensemble_stds}
@@
   \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{offset_ensemble_means.png}
+  \includegraphics[width=\textwidth]{offset_ensemble_means.pdf}
   \caption{}\label{fig:offset_ensemble_means}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{rotated_monomers.png}
+  	\includegraphics[width=\textwidth]{rotated_monomers.pdf}
   	\label{fig:rotated_monomers}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{staggered.png}
+  	\includegraphics[width=\textwidth]{staggered.pdf}
 	\label{fig:staggered}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.png}  %BJC6: I can simplify this more (stacked monomers on each side with a few water molecules in between.
+  	\includegraphics[width=\textwidth]{solvated_pore_cross_section.pdf}  %BJC6: I can simplify this more (stacked monomers on each side with a few water molecules in between.
   	\label{fig:solvated_pore}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.pdf}
   	\label{fig:rotated_monomers_rzplot_restrained}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.png}
+  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.pdf}
   	\label{fig:staggered_rzplot_restrained}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{solvated_pore_rzplot_restrained.png}
+  	\includegraphics[width=\textwidth]{solvated_pore_rzplot_restrained.pdf}
   	\label{fig:solvated_pore_rzplot_restrained}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
+  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.pdf}
   	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png} %BJC5: this needs to be updated
+  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.pdf}
   	\caption{}\label{fig:staggered_rzplot_norestraints} 
@@
   	\centering
-  	\includegraphics[width=\textwidth]{solvated_offset_rzplot_1.png}
+  	\includegraphics[width=\textwidth]{solvated_offset_rzplot_1.pdf}
   	\caption{}\label{fig:solvated_pore_rzplot_norestraints}
@@
   \begin{subfigure}{\textwidth}
-  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
+  \includegraphics[width=\textwidth]{nophenyls_rzplot.pdf}
   \end{subfigure}
@@
   \centering
-  \includegraphics[width=\textwidth]{hbonds_tails.png}
+  \includegraphics[width=\textwidth]{hbonds_tails.pdf}
   \caption{}\label{fig:hbond_visualization}
@@
   \centering
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{regional_density_legend.pdf}
+  \end{subfigure}
   \begin{subfigure}{0.32\textwidth}
-        \includegraphics[width=1\linewidth]{sodium_density.png}
+        \includegraphics[width=1\linewidth]{sodium_density.pdf}
         \caption{Sodium Ions}
@@
   \begin{subfigure}{0.32\textwidth}
-        \includegraphics[width=1\linewidth]{head_group_density.png}
+        \includegraphics[width=1\linewidth]{head_group_density.pdf}
         \caption{Head Groups}
@@
   \begin{subfigure}{0.32\textwidth}
-        \includegraphics[width=1\linewidth]{tails_density.png}
+        \includegraphics[width=1\linewidth]{tails_density.pdf}
         \caption{Tails}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.png}
+  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.pdf}
   	\caption{300K}\label{fig:dihedrals_300K}
@@
   	\centering
-  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.png}
-  	\caption{300K}\label{fig:dihedrals_500K}
+  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.pdf} % Run : torsions.py -t tethered_columns.xtc -g tethered_columns.gro (the appropriate dihedral is the default)
+  	\caption{500K}\label{fig:dihedrals_500K}
   \end{subfigure}
@@
   \centering
-  \includegraphics[width=\textwidth]{xlink_charts.eps}
+  \includegraphics[width=\textwidth]{xlink_charts.pdf}
   \caption{There are minor differences between the physical properties of a

### 2018-09-18 Ben_Manuscripts/structure_paper/figures/xlink_plot.py

@@ -75,5 +75,5 @@ axarr[1, 1].set_xticklabels(labels)
 plt.setp([a.get_xticklabels() for a in axarr[0, :]], visible=False)
 #plt.setp([a.get_yticklabels() for a in axarr[:, 1]], visible=False)
 plt.tight_layout()
-plt.savefig('xlink_charts.eps')
+plt.savefig('xlink_charts.pdf')
 plt.show()

### 2018-09-18 HII/Scripts/tilt.py

@@ -169,7 +169,8 @@ if __name__ == "__main__":
         plt.xlabel('Tilt angle with respect to xy plane', fontsize=14)
         plt.ylabel('Probability', fontsize=14)
         plt.tight_layout()
-        plt.savefig('tilt_dist.png')
+        plt.savefig('tilt_dist.pdf')
+        print('bloop')
         # plt.show()
         # exit()
         # print(all_tilt_angles.shape)
@@ -189,7 +190,7 @@ if __name__ == "__main__":
         plt.xlabel('Time (ps)', fontsize=14)
         plt.ylabel('Tilt angle w.r.t xy plane (degrees)', fontsize=14)
         plt.axes().tick_params(labelsize=14)
-        plt.savefig(args.output)
+        #plt.savefig(args.output)
 
         if not args.noshow:
             plt.show()

### 2018-09-26 Ben_Manuscripts/structure_paper/Draft.tex
Added new figures

@@
 %MRS5: could be punchier. I will keep thinking.  
-\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
+\title{Understanding the nanoscale structure of inverted hexagonal phase lyotropic liquid crystal polymer membranes}
 \author{Benjamin J. Coscia}
-\author{Joe Yelk}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+\author{Joseph Yelk}
 \author{Matthew A. Glaser}
@@
 
-  \begin{tocentry}
-  \end{tocentry}
-
   \begin{abstract}
 
-  Nanostructured porous membranes made from the cross-linked hexagonal phase
-  of self-assembled lyotropic liquid crystals (LLCs) are a promising material
-  for selective separations. In this work, we investigate an experimentally
-  characterized LLC membrane using atomistic molecular modeling. In particular,
-  we compare simulated X-ray diffraction (XRD) patterns with experimental XRD
+  Periodic, nanostructured porous polymer membranes made from the cross-linked 
+  inverted hexagonal phase
+  of self-assembled lyotropic liquid crystals (LLCs) are a promising class of materials
+  for selective separations. In this work, we investigated an experimentally
+  characterized LLC polymer membrane using atomistic molecular modeling. In particular,
+  we compared simulated X-ray diffraction (XRD) patterns with experimental XRD data
   to quantify and understand the differences between simulation and experiment.
-  We find that pores are likely composed of 5 columns of stacked LLC monomers
+  We found that the nanopores are likely composed of 5 columns of stacked LLC monomers
   which surround each hydrophilic core. We learned that these columns likely 
-  move independently of each other over time scales which we can not simulate.
-  We find that some of the structure previously attributed to monomer tail 
+  move independently of each other over time scales that we can not simulate.
+  We also found that some of the structure previously attributed to monomer tail 
   tilt is likely instead due to ordered tail packing. Although this system
@@
   to fully reproduce all features from the experimental XRD pattern due to
-  asymmetries introduced by hydrogen bonds between monomer head groups and
-  water molecules. We explore the composition and structure of the nanopores
+  asymmetries introduced by hydrogen bonds between the monomer head groups and
+  water molecules. Finally, we explored the composition and structure of the nanopores
   and reveal that there exists a composition gradient rather than an abrupt
@@
   in size and smaller, as well as ions. However the porous architecture of
-  commercially available membranes lack uniformity which severely impacts their
+  commercially available membranes lack uniformity, which severely impacts their
   selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
   fabrication involves the spontaneous assembly of polymers into disordered
-  structures which offer separation pathways that are tortuous and polydisperse
+  structures that offer separation pathways that are tortuous and polydisperse
   in size \cite{werber_materials_2016}. Tortuosity increases the effective
-  length that a solute must travel, while polydispersity limits membrane
+  length that a solute must travel, while pore size polydispersity limits membrane
   selectivity.
@@
 
-  Nanostructured porous membrane materials have become an increasingly popular
+  Ordered, nanostructured porous membrane materials have become an increasingly popular
   research area for aqueous separations applications because they offer the 
@@
   permitting the design of solute-specific separation membranes 
-  \cite{humplik_nanostructured_2011}. However their development has been 
+  \cite{humplik_nanostructured_2011}. However, their development has been 
   limited by the ability to synthesize and scale various technologies. Graphene
-  sheets are atomically thick which results in excellent water permeability but
+  sheets are atomically thick, which results in excellent water permeability but
   defects during manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
@@
 
-  Preliminary evidence has shown that crosslinked lyotropic liquid crystal
+  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
   (LLC) membranes are scalable and may be capable of performing highly selective
@@
   self-assemble into porous nanostructures \cite{smith_ordered_1997} and can be
-  crosslinked to create mechanically strong membrane films with pores on the
-  order of 1 nm in diameter \cite{zhou_supported_2005}. Unlike most commercial NF
-  membranes, LLC membrane pores are uniform in size because they are
-  self-assembled. Since LLC membranes lack a pore size distribution, they
+  cross-linked to create mechanically strong membrane films with periodic pores on the
+  order of 1 nm in diameter \cite{zhou_supported_2005}. Unlike the pores in most commercial NF
+  membranes, polymeric LLC membrane pores are uniform in size because they are
+  formed by self-assembly. Since LLC polymer membranes lack an appreciable pore size distribution, they
   inherently exhibit high selectivity due to their strict molecular weight
@@
 
-  The feasibility of nanostructured LLC membranes for selective separations has
-  been demonstrated using LLCs that form the type 1 bicontinuous cubic
+  The feasibility of nanostructured LLC polymer membranes for selective separations has
+  been demonstrated using LLC monomers that form the type 1 bicontinuous cubic
   (Q\textsubscript{I})
@@
   and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
-  phases. When separating organic solutes from NaCl, Q\textsubscript{I} phase
+  phases. When separating organic solutes from NaCl, Q\textsubscript{I}-phase
   membrane filtration experiments have shown selectivity 2--3 times higher than
@@
   \cite{dischinger_application_2017}. When separating a series of various sized
-  dyes, the H\textsubscript{II} phase membrane showed complete rejection of dyes
+  dyes, the H\textsubscript{II}-phase membrane showed complete rejection of dyes
   bigger than 1.2 nm in size \cite{zhou_supported_2005}.
 
-  The H\textsubscript{II} phase pore geometry (Figure~\ref{fig:assembly}) has a
+  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:assembly}) has a
   higher theoretical capacity for transport than the Q\textsubscript{I} phase.
   The H\textsubscript{II} phase forms at room temperature in the presence of
-  c.a.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
+  ca.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
   columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
-  form the same hexagonal columnar structure which, in literature, has been
+  form the same hexagonal columnar structure which, in the literature, has been
   referred to as the Col\textsubscript{h} thermotropic
@@
 %  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
-  Q\textsubscript{I} phase membranes consist of a tortuous network of three
+  Q\textsubscript{I}-phase membranes consist of a tortuous network of three
   dimensionally interconnected pores that prevent optimal through-plane
   transport. In contrast, the densely packed, non-tortuous and uniform sized
-  pores of H\textsubscript{II} phase membranes represent the ideal geometry for
+  pores of H\textsubscript{II}-phase membranes represent the ideal geometry for
   achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.  However, the
-  hexagonally packed liquid crystalline domains of the H\textsubscript{II} phase
-  generally form isotropically oriented and therefore mutually unaligned domains
+  hexagonally packed LC domains of the H\textsubscript{II}-phase
+  generally form mutually unaligned domains,
   which are detrimental to membrane permeability. This domain scale misalignment
@@
   However, recently researchers have learned how to macroscopically align the
-  hexagonal domains which has revived research into H\textsubscript{II} phase LLC
-  membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
-  hexagonal domains, created by the monomer Na-GA3C11, using a magnetic field
+  hexagonal domains which has revived research into H\textsubscript{II}-phase LLC
+  polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
+  domains, created by the "dry" monomer Na-GA3C11, using a magnetic field
   with subsequent cross-linking to lock the structure in
   place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could
-  obtain the same result by confining neat monomer between PDMS or glass
+  also obtain the same result by confining the neat monomer between PDMS or glass
   substrates since hexagonal mesophases preferentially anchor perpendicular to
@@
 
-  Our current understanding of the molecular details of LLC membranes'
+  Our current understanding of the molecular details of resulting LLC polymer membranes'
   nanostructure is not sufficient to be able to precisely design them for
@@
   that correlates the physiochemical properties of the counterion used in a 
-  Q\textsubscript{I} phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
+  Q\textsubscript{I}-phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
   Although their model showed some qualitative agreement with experiment, the
   quality of fit of their model was limited due to complex solute-membrane 
-  interactions which could not easily be modeled. Additionally, they observed
+  interactions that could not easily be modeled. Additionally, they observed
   an unexpected discrepancy in the relationship between uncharged solute
-  rejection and water permeability which will require a more in-depth knowledge of
+  rejection and water permeability, which will require a more in-depth knowledge of
   the difference between solute and solvent transport.
@@
   Over the past 20 years, H\textsubscript{II}-phase LLC
-  polymer membrane studies have been limited primarily to Na-GA3C11 with some
-  characterization done after minor structural modifications. Resel et al.~varied
-  the length of the monomer tails and the counterion used and observed its effect
+  polymer membrane studies have been limited primarily to the Na-GA3C11 monomer with some
+  characterization done after minor structural modifications. For example, 
+  Resel et al.~varied the length of the monomer tails and the counterion used and observed its effect
   on pore spacing \cite{resel_structural_2000}.  In a later study of rejection
@@
 
-  A molecular-level understanding of LLC membrane structure, enabled by
+  A molecular-level understanding of LLC polymer membrane structure, enabled by
   molecular dynamics (MD) simulations, can provide guidelines to reduce the large
@@
   membranes. Useful molecular-level modeling should incorporate a detailed picture of the
-  nanoscopic pore structure which is crucial to understanding the role of
+  nanoscopic pore structure, which is crucial to understanding the role of
   monomer structure in solute transport and membrane design. 
@@
   With such an atomistic model, we can directly observe molecular-level solute
-  transport and suggest governing mechanisms. We can observe how the choice of
-  head group interacts with solutes of interest. We can interchange
+  transport and suggest governing mechanisms. We can also observe how the choice of
+  head group interacts with solutes of interest. In addition, we can interchange
   counterions which may influence both the pore size and the strength of the
@@
 
-  In this study, we achieve a  more realistic atomistic description of LLC
-  membranes than, to our knowledge, has ever previously been created, and explore
+  In this study, we achieve a  more realistic atomistic description of hexagonal LLC
+  polymer membranes than, to our knowledge, has ever previously been created, and explore
   what new structural information can be gained and what structure hypotheses are
@@
   information as possible. We are most interested in reproducing the conclusions
-  about structure drawn from small angle X-ray scattering (SAXS) and wide angle
-  X-ray scattering (WAXS) experiments as well as in matching ionic conductivity
+  about structure drawn from small-angle X-ray scattering (SAXS) and wide-angle
+  X-ray scattering (WAXS) experiments, as well as in matching ionic conductivity
   measurements \cite{feng_thin_2016}.
@@
     based on limited chemical and experimental data. (b) We use detailed molecular 
-    modeling in this paper in order to appropriately model the pore's complex architecture
+    modeling in this paper in order to appropriately model the pore's complex architecture,
     which is crucial to understanding the mechanism of solute transport. In both 
@@
   In this paper, we perform molecular modeling of the Col\textsubscript{h}
-  assembly formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the
+  thermotropic (i.e., solvent-free) assembly formed by Na-GA3C11. Compared to 
+  the lyotropic (i.e, solvent-containing) H\textsubscript{II} phase, the
   Col\textsubscript{h} phase is a simpler starting point. The system is not
@@
   there exists detailed experimental characterization of the fully aligned state,
-  including 2D wide-angle X-ray scattering (WAXS) patterns
-  (Figure~\ref{fig:WAXS}) which are useful for reconstructing structural data.
+  including 2D-WAXS patterns (Figure~\ref{fig:WAXS}) that are useful for 
+  reconstructing structural data.
 
@@
 	is related to the distance between pores. We observe the same information
-	with higher resolution by looking at the same system's 1D SAXS pattern 
+	with higher resolution by looking at the same system's 1D-SAXS pattern 
 	(Fig.~\ref{fig:SAXS}).
@@
         \end{subfigure}
-	\caption{(a) 2D WAXS gives details about repeating features on the
+	\caption{(a) 2D-WAXS gives details about repeating features on the
 		order of angstroms. Experimentalists have explained each of the 5 major
@@
 		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
-		from \citenum{feng_thin_2016}) The repeat spacing in the 1D small angle X-ray
+		from \citenum{feng_thin_2016}) The repeat spacing in the 1D-SAXS
 		scattering pattern is characteristic of hexagonal packing. The leading peak,
@@
 
-	\item What structural motif best matches experimental 2D WAXS patterns?\label{point:xrdmatch}
+	\item What structural motif best matches experimental 2D-WAXS patterns?\label{point:xrdmatch}
 
@@
 	While the Col\textsubscript{h} phase is described as dry, it is likely
-	that small amounts of ambient water are absorbed into the system. The hydrogen
-	bonding network formed by the water may play a role in structuring the pore. We
-	used simulated X-ray diffraction (XRD) patterns to uncover any 
-        %see if there is any
+	that small amounts of ambient water are absorbed into the system. The 
+	hydrogen-bonding network formed by the water may play a role in structuring 
+	the pore. We used simulated X-ray diffraction (XRD) patterns to uncover any 
 	meaningful structural difference between a ``dry" and a ``wet" system.
@@
   configurations by applying a simulated annealing process to a
-  parameterized monomer. We cooled monomers from 1000K to 50K over 10
-  nanoseconds. We randomly pulled a low energy configuration from the
+  parameterized monomer. We cooled monomers from 1000 K to 50 K over 10
+  ns. We randomly pulled a low energy configuration from the
   trajectory then reassigned charges using \texttt{molcharge}. Using the new
@@
   configuration from the trajectory which we used for full system
-  construction (Figure~\ref{fig:build_procedure}a). See section S-\ref{S-section:parameterization} 
-  for further detail of the parameterization process.
+  construction (Figure~\ref{fig:build_procedure}a). See Section S-\ref{S-section:parameterization} 
+  of the Supporting Information for further detail of the parameterization process.
 
@@
   \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system (see section S-\ref{S-section:self_assembly}). 
-  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
+  indicators of progress towards an ordered system (see Section S-\ref{S-section:self_assembly} of the 
+  Supporting Information). 
+  To bypass the slow self-assembly process, we used Python scripts to assemble monomers
   into a structure close to one of a number of hypothesized equilibrium configurations
@@
   \end{subfigure}
-  \caption{(a) We parameterized a single monomer and annealed it to produce a low energy
+  \caption{(a) We parameterized a single monomer and annealed it to produce a low-energy
 		configuration. (b) We assembled monomers into columns by stacking them on top of each 
@@
   and to obtain sufficient resolution when simulating XRD patterns (see further discussion
-  in section S-\ref{S-section:monomers_per_column}).
+  in Section S-\ref{S-section:monomers_per_column} of the Supporting Information).
 
@@
   of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
-  %MRS13: be consistent on capitalization of ``Supporting'' ``Information'' and ``section''. Look at JPCB for guidance.
-  Supporting information, section S-\ref{S-section:initial_config_dependence}. The 
+  Supporting Information, Section S-\ref{S-section:initial_config_dependence}. The 
   distance between vertically stacked monomers, the xy position of monomers with respect 
@@
   \AA. However this largest spacing yields non-physical behavior which is detailed in the 
-  Supporting Information, section S-\ref{S-section:initial_dbwl}.
+  Supporting Information, Section S-\ref{S-section:initial_dbwl}.
 
@@
 
-  We developed equilibration schemes for creating dry and wet configurations.
+  We developed equilibration schemes for creating dry (i.e. thermotropic LC phase)
+  and wet (i.e. LLC phase) configurations.
   Both schemes start with an initial configuration generated according to the
@@
   structure to equilibrate for 5 ns in the NPT ensemble with pressure controlled
-  by the Berendsen barostat followed by NPT equilibration simulations run for at
+  by the Berendsen barostat, followed by NPT equilibration simulations run for at
   least 400 ns using the Parrinello-Rahman barostat. More equilibration details
-  are given in section S-\ref{S-section:equilibration}.
+  are given in Section S-\ref{S-section:equilibration} of the Supporting Information.
 
@@
   ions in their respective pores. We generated pore spacing statistics 
-  using the bootstrapping technique (See section S-\ref{S-section:p2p_stats} of the
+  using the bootstrapping technique (See Section S-\ref{S-section:p2p_stats} of the
   Supporting Information). 
-  % BJC15: added to address Matt's concern
   The pore spacings calculated in this way are consistent
-  with one half of the $x$ and $y$ box vectors (See, Table S-\ref{S-table:p2p}). However
-  our method for their calculation does a better job capturing the spread of 
-  pore-to-pore distances.
+  with one half of the $x$ and $y$ box vectors (See, Table S-\ref{S-table:p2p} in the
+  Supporting Information). However, our method for their calculation does a better 
+  job capturing the spread of pore-to-pore distances.
 
@@
   cross-section of the patterns at $q_z$=0 (Figure~\ref{fig:saxs_xsection}). The
-  beamstop covers most of the small angle reflections in the experimental 2D WAXS
+  beamstop covers most of the small angle reflections in the experimental 2D-WAXS
   pattern. In order to compare the simulated intensity of R-pores to experiment,
-  we used the $q_r$ cross-section of 2D SAXS which was generated from the same
-  sample (Figure S-\ref{S-fig:2DSAXS}). Since the d\textsubscript{200} peak is
-  partially exposed in the experimental 2D WAXS pattern, we normalized the
-  experimental 2D SAXS cross-section by matching the intensity of the
-  d\textsubscript{200} peak between it and the experimental 2D WAXS
-  cross-section. It is possible that the peak is not fully captured in the 2D
-  WAXS pattern and that we have underestimated the intensity of R-pores in the
+  we used the $q_r$ cross-section of 2D-SAXS which was generated from the same
+  sample (Figure S-\ref{S-fig:2DSAXS} of the Supporting Information). Since the d\textsubscript{200} peak is
+  partially exposed in the experimental 2D-WAXS pattern, we normalized the
+  experimental 2D-SAXS cross-section by matching the intensity of the
+  d\textsubscript{200} peak between it and the experimental 2D-WAXS
+  cross-section. It is possible that the peak is not fully captured in the 2D-WAXS
+  pattern and that we have underestimated the intensity of R-pores in the
   experimental pattern.
@@
   \end{equation}
-  where A is a fitting parameter for amplitude, $z$ is the independent variable of $g(z)$ 
+  where A is a fitting parameter for amplitude, $z$ is the independent variable of $g(z)$, 
   and L is the fit correlation length. We calculated the error in the estimated value
@@
   atoms in each group from the pore centers, then normalized by the volume of the
-  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}).
+  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}
+  of the Supporting Information).
 
@@
   atomistic simulations. The quenched disorder is greater in  magnitude than thermal 
-  disorder (See Table~\ref{table:quenched_disorder} in section~\ref{section:rpi}).
-  %MRS13: you just said this already, commenting out.
-  %and inherently includes thermal disorder due to the way we calculate it.
+  disorder (See Table~\ref{table:quenched_disorder} in Section~\ref{section:rpi}).
   This method assumes that the timescales for large scale rearrangements of the
@@
   concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
-  temperature, $T$: 
+  absolute temperature, $T$: 
   \begin{equation}
@@
   We based our cross-linking algorithm on the known reaction mechanism 
-  (Figure S-\ref{S-fig:xlink_mech}). The reaction takes place at the terminal vinyl groups
+  (Figure S-\ref{S-fig:xlink_mech} of the Supporting Information). The reaction 
+  takes place at the terminal vinyl groups
   on each alkane tail. The procedure is carried out iteratively. Each iteration, the
@@
   spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional 
-  systems with monomers initially spaced 5 \AA~apart vertically (see section~\ref{S-section:initial_pore_spacing}
+  systems with monomers initially spaced 5 \AA~apart vertically (see Section~\ref{S-section:initial_pore_spacing}
   of the Supporting Information for more details on sensitivity to initial layer spacing). 
-  We considered the pore-to-pore spacing to be equilibrated as defined in section~\ref{method:equil_time}.
+  We considered the pore-to-pore spacing to be equilibrated as defined in Section~\ref{method:equil_time}.
   Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested.
@@
   monomers, monomer head groups have more rotational freedom. We quantified the ordering of
-  the head groups using the nematic order parameter (see section S-\ref{S-method:nematic_order}
+  the head groups using the nematic order parameter (see Section S-\ref{S-method:nematic_order}
   for details of calculation). Disordered basin systems have a lower nematic order parameter 
@@
 
-  \subsection{Simulated XRD comparison to 2D WAXS data}
-
-  We can better understand the structure of the system by simulating X-ray
-  diffraction patterns produced from equilibrated MD trajectories (see
+  \subsection{Simulated XRD comparison to 2D-WAXS data}
+
+  We can better understand the structure of the system by simulating XRD
+  patterns produced from equilibrated MD trajectories (See
   section~\ref{method:xrd}) and comparing them to experiment, addressing
@@
   300 K in the ordered and disordered basins, as those were the most consistent
-  with the most unambiguous X-ray diffraction features, the pore-to-pore spacing
+  with the most unambiguous XRD features, the pore-to-pore spacing
   and the stacking distance.  We generated simulated patterns using the locally
@@
   Section~\ref{method:equil_time}). There are two important factors to take into
-  account when looking at differences between experimental XRD and simulated XRD.
+  account when looking at differences between experimental and simulated XRD patterns.
   First, the simulated diffraction patterns have some noise, especially along the
@@
   \begin{itemize}
-  	\item The origin of R-spots (section~\ref{section:rspots})
-  	\item The position, shape and intensity of R-$\pi$ (section~\ref{section:rpi})
-  	\item The origin of R-double (section~\ref{section:rdouble})
+  	\item The origin of R-spots (Section~\ref{section:rspots})
+  	\item The position, shape and intensity of R-$\pi$ (Section~\ref{section:rpi})
+  	\item The origin of R-double (Section~\ref{section:rdouble})
   \end{itemize}
@@
   R-alkanes is the experimental feature most likely to be reproduced by our
-  simulations.  We reach this conclusion because alkane parameters in GAFF and
+  simulations.  We reached this conclusion because alkane parameters in GAFF and
   AMBER forcefields generally reproduce data well.~\cite{wang_development_2004,caleman_force_2012}
@@
   systems. Some or all of this discrepancy may be a consequence of our
-  normalization of the experimental 2D SAXS pattern, since the common peak
-  between it and the 2D WAXS patterns is partially obscured by the beamstop in
+  normalization of the experimental 2D-SAXS pattern, since the common peak
+  between it and the 2D-WAXS patterns is partially obscured by the beamstop in
   the WAXS. If our simulations do indeed predict an intensity of R-pores that is
@@
   respect to the membrane plane. We found that it equilibrates to an average tilt
-  angle of -2\degree~(Fig.~\ref{fig:tilt}), far from the 37\degree~tilt angle
+  angle of -2\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle
   previously used to explain R-spots. Even when we placed position restraints on
@@
   tilt relative to the $xy$ plane to an angle statisically indistinguishable from
-  zero (See Section~S-\ref{S-section:tail_tilt}).
+  zero (see Section~S-\ref{S-section:tail_tilt} of the Supporting Information).
 
   In order to more clearly identify the structural reasons for R-spots, we
-  equilibrated an ordered basin sandwiched configuration at 280K to moderately
+  equilibrated an ordered basin sandwiched configuration at 280 K to moderately
   increase the order and therefore intensity.  Many force fields do not obtain
@@
   ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
-  our membrane system, simulated at 300K, is under-structured in the tail region
-  compared to the experimental structure at 300K. We found that lowering the
+  our membrane system, simulated at 300 K, is under-structured in the tail region
+  compared to the experimental structure at 300 K. We found that lowering the
   temperature indeed better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
@@
   distribution of these angles located ca. $-60\degree$, $0\degree$,
-  and $60\degree$ which is consistent with a hexagonally packed
+  and $60\degree$, which is consistent with a hexagonally-packed
   configuration (Figure~\ref{fig:layered_tails}).  This ordering is
@@
   off at the tail ends, where there is more space to fill causing them
-  to pack nearly isotropically. See Section~S-\ref{S-section:tail_packing} for
+  to pack nearly isotropically. See Section~S-\ref{S-section:tail_packing} 
+  of the Supporting Information for
   a more detailed explanation of the calculation and packing
@@
   The peaks in the nearest neighbor angle distribution due to the hexagonal
-  packing are consistent with the location of R-spots. The 2D Fourier transform
+  packing are consistent with the location of R-spots. The 2D-Fourier transform
   of a simple hexagonal array constructed based on the peak angles in
@@
 
-  \subsubsection{The position, shape and intensity of R-$\pi$}\label{section:rpi}
-
-  The position, shape and intensity of R-$\pi$, generated from simulations at
+  \subsubsection{The position, shape, and intensity of R-$\pi$}\label{section:rpi}
+
+  The position, shape, and intensity of R-$\pi$, generated from simulations at
 %  300K, are qualitatively similar to experiment, but have significant
@@
   greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
-  basins at the high part of that range and are on average 0.2 and 0.3 \AA~more
-  distant. This behavior is not surprising since GAFF models atoms as point charges and
+  basins at the high end of that range.% and are on average 0.2 and 0.3 \AA~more distant.
+  This behavior is not surprising since GAFF models atoms as point charges and
   does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
@@
   necessarily more tightly packed configuration. We equilibrated the
-  system at 500 K then annealed it to 300 K in an attempt to coerce the tails
+  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
   into a more tightly packed configuration. Before annealing and in order to
@@
   adjacent columns. We saw no improvement in packing distance over our 300 K
-  models (See further discussion in section~\ref{section:slow_dynamics}).
+  models (see further discussion in Section~\ref{section:slow_dynamics}).
 
@@
   deviations of the monomers from their average positions during the 
-  production simulations. We hypothesize that, experimentally, the quenched disorder is the 
-  same as thermal disorder, but we cannot reach the necssary transition
-  timescales to fully thermalize in these simulations.  
-  %MRS12: when reworking the first part of the simulation, our hypothesis for the REASONS behind the quenched disorder will ahave to be addressed.
-The two options are 1) the quenched disorder is just thermal disorder whose transition timescales we can't reach, and 2) the system if simulated for miliseconds/seconds would still be glassy.
-It PROBABLY should go before here, when it's first described.
-  %BJC12: I first describe in methods, which seems the wrong place to put that hypothesis, so I tacked it on here.
+  production simulations. 
+  %We hypothesize that, experimentally, the quenched disorder is the 
+  %same as thermal disorder, but we cannot reach the necessary transition
+  %timescales to fully thermalize in these simulations.
 
@@
   Increasing thermal noise in the $z$-direction will reduce the intensity
-  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
+  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increased the
   thermal noise of the simplified parallel displaced system in the $z$-direction by
-  12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of 
+  12\% and 27\%, we saw a 3 and 15-fold decrease in the maximum intensity of 
   R-$\pi$ respectively (Figure~\ref{fig:znoise}). Despite the decrease in 
@@
 
-  However, when we allow monomer columns to move independently in the
+  However, when we allowed monomer columns to move independently in the
   $z$-direction, the intensity of R-$\pi$ drops and the $q_r$ cross-section of
@@
   right amount of disorder on the $xy$ plane. However, the relatively low quality
-  of the fit implies that the FWHM may be incorrect, and that the radial ordering
-  of the head groups may benefit from further optimization.
+  of the fit implies that the FWHM may actually be different from experiment, and
+  that the radial ordering of the head groups may benefit from further optimization.
   %MRS12: is there a structral 
@@
   configurations. We used the same equilibration scheme as above 
-  (see section~\ref{section:equilibration}). However, we built the 
+  (see Section~\ref{section:equilibration}). However, we built the 
   initial configurations with randomly displaced columns in the 
@@
   Figure~\ref{fig:offset_ensemble_pooled} 
-  (see section~\ref{method:simple_systems}). The distributions appear 
+  (see Section~\ref{method:simple_systems}). The distributions appear 
   symmetric meaning that there is an equal chance for a head group to displace
-  in the positive or negative $z$, $r$ or $\theta$-direction. We verified that
+  in the positive or negative $z$, $r$, or $\theta$-direction. We verified that
   this is the case for individual COMs. 
@@
   the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
-  (See Figure~S-\ref{S-fig:between_pd}). In this way, columns can more easily act 
+  (see Figure~S-\ref{S-fig:between_pd} of the Supporting Information). In this way,
+  columns can more easily act 
   independently while maintaining some features of parallel displaced structure.
@@
   barrier that prevents rotation of carboxylate groups attached to phenyl rings
-  since the group extends the system's $\pi$ conjugation ~\cite{carey_organic_2011} (See Figure
-  S-\ref{S-fig:carboxylate_dihedral_rb}), which is significant even considering
+  since the group extends the system's $\pi$ conjugation ~\cite{carey_organic_2011} (see Figure
+  S-\ref{S-fig:carboxylate_dihedral_rb} of the Supporting Information), which is significant even considering
   possible overestimates of the barrier height in the classical force field. 
@@
   Another way to produce R-double is if we rotate monomers with respect to
-  vertically adjacent monomers. In this configuration, monomers are rotated so
+  vertically adjacent monomers. In this configuration, the LLC monomers are rotated so
   that the vector created by the bond extending from the carboxylate carbon to
@@
 
-  We can also produce R-double if monomers are not uniformly spaced in the
+  We can also produce R-double if the LLC monomers are not uniformly spaced in the
   $z$-direction, but instead form pairs that stack less than 3.7~\AA~apart, with
-  COMs that are spaced 7.4 \AA~ from neighboring pairs of monomers (Figure
-  ~\ref{fig:staggered_rzplot_norestraints}). 
+  COMs that are spaced 7.4 \AA~ from neighboring pairs of monomers 
+  (Figure~\ref{fig:staggered_rzplot_norestraints}). 
   %MRS12: not sure this is necessary.
@@
   Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows
-  R-double to appear. If a monomer head group shares a hydrogen bonded water
+  R-double to appear. If a monomer head group shares a hydrogen-bonded water
   molecule with a head group above itself, it will be less likely to share a
@@
   by water molecules as described above since it is the only mechanism that can
-  be observed without position restraints. The extent of the hydrogen bonding
+  be observed without position restraints. The extent of the hydrogen-bonded
   network that forms is largely determined by the accuracy of the forcefield. It
@@
 
-  \subsection{Atomistic structure of pore columns}
+  \subsection{Atomistic structure of the pore columns}
 
@@
   region, we used heavy atoms making up the aromatic rings and carboxylate groups. For the tail
-  region we used carbon atoms of the monomer tails (See Figure S-\ref{S-fig:monomer_color_coded}
-  for a diagram). We averaged the histograms over at least 50 ns of equilibrated trajectory.
+  region, we used carbon atoms of the monomer tails (See Figure S-\ref{S-fig:monomer_color_coded}
+  of the Supporting Information for a diagram). We averaged the histograms over at least 50 ns of equilibrated trajectory.
 
@@
   We measured the diffusion constants of monomers in each of the systems we
-  studied (See Table S-\ref{S-table:msd}) and learned that they are all on the order of
+  studied (see Table S-\ref{S-table:msd} of the Supporting Information) and learned that they are all on the order of
   $10^{-14}~m^2/s$. However, since on this timescale, no monomers move
@@
   head groups and the ether oxygens which attach the tails to the head group 
-  (See Figure S-\ref{S-fig:dihedrals}). We exclude the dihedral from the middle tail 
+  (see Figure S-\ref{S-fig:dihedrals} of the Supporting Information). We exclude the dihedral from the middle tail 
   since it is fundamentally different than the two symmetric outside tails. We 
@@
   to 8.87 nm, which is roughly consistent with the stacking distance reported in 
-  Table~\ref{table:correlation_length}. After 200 ns of annealing from 500K to 300K, the 
+  Table~\ref{table:correlation_length}. After 200 ns of annealing from 500 K to 300 K, the 
   $z$-dimension of the unit cell was 9.22 nm. We repeated the annealing procedure over the 
@@
   relationship using the collective diffusion model\cite{liu_collective_2013} 
-  (See section S-\ref{S-fig:conductivity}). The values calculated by the 
+  (see section S-\ref{S-fig:conductivity} of the Supporting Information). The values calculated by the 
   collective diffusion model agree with Nernst-Einstein values within error, 
@@
   we simulated infinitely long, aligned pores. The ionic conductivity measurement 
-  to which we are comparing was done with an \SI{80}{\micro\metre} thick film, 
+  to which we are comparing was done with an \SI{80}{\micro\metre}-thick film, 
   nearly 10,000 times thicker than our simulated
@@
   displaced configurations in the ordered pore basin. We allowed the cross-linking
-  algorithm to propagate until greater than 90\% of vinyl groups were either involved
-  in a cross-linking reaction or were terminated (see section S-\ref{S-section:xlink}
+  algorithm to propagate until greater than 90\% of the vinyl groups on the tails of the 
+  monomers were either involved in a cross-linking reaction or were terminated 
+  (see Section S-\ref{S-section:xlink} of the Supporting Information)
   for further details of the cross-linking algorithm). We allowed the cross-linked
@@
   We achieve maximum structural consistency with experiment, as determined by
-  simulated 2D XRD patterns, when we build our model in the ordered basin
+  simulated 2D-XRD patterns, when we build our model in the ordered basin
   parallel displaced configuration with 5 monomer columns per pore and 1 wt\%
@@
 
+  \section*{Acknowledgements}
+
+  J. Y. and M. A. G. were supported by the Soft Materials Research Center under NSF 
+  MRSEC Grant DMR-1420736
+
+  Molecular simulations were performed using the Extreme Science and Engineering Discovery
+  Environment (XSEDE), which is supported by National Science Foundation grant number 
+  ACI-1548562. Specifically, it used the Bridges system, which is supported by NSF award
+  number ACI-1445606, at the Pittsburgh Supercomputing Center (PSC). Simulations were also
+  performed on Summit super computer, which is supported by the NSF grant OAC-1532235. 
+  This work was supported financially by NSF through the grant NSF-CBET 1351635.
+
+  The authors thank Richard Noble, Michael McGrath, Gregory Dwulet and Sarah Dischinger
+  for useful discussions that enhanced our understanding of these LC membrane systems.
+
+  \section*{Supporting Information}
+
+  Detailed explanations and expansions upon the results and procedures mentioned in 
+  the main text are described in the Supporting Information. This information is 
+  available free of charge via the Internet at http://pubs.acs.org.
+
   \clearpage
   \bibliography{llc}
+
+  \newpage
+  %BJC: TOC graphic
+
+  \section*{Graphical TOC Entry}
+  \begin{figure}
+  \includegraphics[width=4.07cm]{toc_waxs.pdf}
+  \includegraphics[width=4.5cm]{toc_image_final.pdf}
+  \end{figure}
 

### 2018-09-26 Ben_Manuscripts/structure_paper/cover_letter.tex
Added new figures

\documentclass[fontsize=11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{hyperref}
\usepackage[export]{adjustbox}
\usepackage{anyfontsize}

\begin{document}

	\graphicspath{{./figures/}}

	%BJC: check address, phone number and fax (?) number
	\begin{figure}
	\centering
	\begin{minipage}{0.37\textwidth}
	\includegraphics[width=2.14in,left]{CUBoulder.pdf}
	\end{minipage}
	\begin{minipage}{0.62\textwidth}
	\scriptsize
	\noindent Department of Chemical and Biological Engineering \hfill t 303-735-7860~~~~~~~~~~~~~~~~~~ \\
	\noindent JSCBB, 596 UCB \hfill f 303-735-7860~~~~~~~~~~~~~~~~~~ \\
	\noindent Boulder, Colorado 80309 \hfill michael.shirts@colorado.edu \\
	\end{minipage}
	\end{figure}

	\noindent 10/1/2018\\

	\noindent Dear Editors,\\

	We are submitting ``Understanding the Nanoscale Structure of Inverted Hexagonal 
	Phase Lyotropic Liquid Crystal Polymer Membranes'' by Benjamin J. Coscia (graduate
	student), Joseph Yelk (graduate student), Matthew A. Glaser (professor), Douglas
	L. Gin (professor), Xunda Feng (post-doc) and Michael R. Shirts (professor), for
	consideration for publication as an Article in the Journal of Physical Chemistry
	B. We expect this work to be of significant interest to researchers who study 
	nanostructured polymer membranes for aqueous separations.

	This article studies the atomistic structure of an inverted hexagonal phase 
	self-assembled lyotropic liquid crystal (LLC) polymer membrane. To create these
	materials, liquid crystal (LC) monomers self-assemble into ordered, uniform-sized
	and hexagonally-packed nanopores. The nm-sized pore centers are charged and hydrophilic 
	in nature which makes this type of membrane useful for highly selective aqueous 
	separations of small solutes. By tuning the shape, size and chemical functionality
	of LC monomers, one can intelligently design the pore environment. However,	our 
	current understanding of the nanoscopic pore structure is not yet adequate for us to
	be able to controllably design membranes for solute-specific separations.

	%BJC: following is quite similar to the abstract
	In this paper, we used molecular dynamics (MD) simulations in order to model an
	experimentally characterized LLC polymer membrane and learn about its atomistic
	structure in detail. We simulated XRD patterns from the MD simulation trajectories
	for comparison to experimental 2D wide-angle X-ray scattering (WAXS) and 1D 
	small-angle X-ray scattering patterns. While trying to match our simulated patterns
	to experimental patterns, we found that 5 columns of stacked LLC monomers are 
	likely to pack around the hydrophilic core of each pore. We learned that these 
	columns likely move independently of each other	over time scales that we can not
	simulate. We also found that some of the structure previously attributed to monomer
	tail tilt is likely instead due to ordered tail packing. Although the system studied
	has been reported as ``dry", we show that small amounts	of water are necessary to 
	fully reproduce all features from the experimental 2D-WAXS pattern due to asymmetries
	introduced by hydrogen bonds between the LC monomer head groups and water molecules.
	Finally, we explored the composition and structure of the nanopores and reveal that
	there exists a composition gradient rather than an abrupt partition between the 
	hydrophilic and hydrophobic regions. The clearer picture of the nanoscopic structure
	of these membranes provided in this study will enable a better understanding of the
	mechanisms of small molecule transport within these nanopores. \\

	%BJC: subject to change
	\noindent Some suggestions for reviewers are:
	\begin{enumerate}
		\item Chinedum Osuji has published work related to the synthesis and physical
		properties of the same inverted hexagonal phase LLC membrane studied in our 
		work (University of Pennsylvania, 215-573-3608, 
		\href{mailto:cosuji@seas.upenn.edu}{cosuji@seas.upenn.edu}). 
		\item Menachem Elimelech is a leader in the development of membrane technologies
		for	water desalination and water reuse (Yale University, 203-432-2789, 
		\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).
		\item Arun Yethiraj has studied molecular simulations of the self-assembly
		of liquid crystals into ordered nanostructures, including the type studied
		in our work. (Univeristy of Wisconsin Madison, 608-262-0258, 
		\href{mailto:yethiraj@chem.wisc.edu}{yethiraj@chem.wisc.edu})  % questionable due to related self-assembly research.
	\end{enumerate}

	%BJC: Other reviewer ideas:
	% Jason Bara - University of Alabama -- former member of Gin/Noble group who worked on
	% bicontinuous cubic phase at one point. He helped me figure out how to print the 3D models
	% Jeff McCutcheon - My undergrad advisor. Advised by Elimelech for his PhD.
	% Benoit Roux?
	% Eric Jankowski - Boise State, met at FOMMS. One of his students works with simulated XRD patterns. I actually think this is a much better idea than Yethiraj

	\noindent Please send correspondence regarding this paper to Michael R. Shirts (contact
	details in letterhead).\\

	\noindent Sincerely,

	\noindent Michael R. Shirts \\
    \noindent Benjamin J. Coscia \\
    %BJC: so many authors, it runs off the page. Can just say "Sincerely, the authors" or list names on single line separated by commas.
    and co-authors
    %\noindent Joseph Yelk \\
    %\noindent Matthew A. Glaser
    %\noindent Douglas L. Gin \\
    %\noindent Xunda Feng \\

\end{document}

### 2018-09-27 Ben_Manuscripts/structure_paper/cover_letter.tex
pass at the cover letter.

@@
 	\noindent Department of Chemical and Biological Engineering \hfill t 303-735-7860~~~~~~~~~~~~~~~~~~ \\
-	\noindent JSCBB, 596 UCB \hfill f 303-735-7860~~~~~~~~~~~~~~~~~~ \\
+	\noindent 596 UCB \hfill f 303-735-7860~~~~~~~~~~~~~~~~~~ \\
 	\noindent Boulder, Colorado 80309 \hfill michael.shirts@colorado.edu \\
@@
 
-	\noindent 10/1/2018\\
+	\noindent October 1st, 2018\\
 
+	%MRS: I shortened this a bit and made it more direct; was a bit long.
 	\noindent Dear Editors,\\
-
+	%MRS: don't need to put they are graduate students or postdics. 
 	We are submitting ``Understanding the Nanoscale Structure of Inverted Hexagonal 
-	Phase Lyotropic Liquid Crystal Polymer Membranes'' by Benjamin J. Coscia (graduate
-	student), Joseph Yelk (graduate student), Matthew A. Glaser (professor), Douglas
-	L. Gin (professor), Xunda Feng (post-doc) and Michael R. Shirts (professor), for
+	Phase Lyotropic Liquid Crystal Polymer Membranes'' by Benjamin J. Coscia, Joseph Yelk, Matthew A. Glaser, Douglas
+	L. Gin, Xunda Feng, and Michael R. Shirts, for
 	consideration for publication as an Article in the Journal of Physical Chemistry
@@
 
-	This article studies the atomistic structure of an inverted hexagonal phase 
+        %MRS: maybe ``examines'' instead of studies. 
+	This article examines the atomistic structure of an inverted hexagonal phase 
 	self-assembled lyotropic liquid crystal (LLC) polymer membrane. To create these
@@
 	separations of small solutes. By tuning the shape, size and chemical functionality
-	of LC monomers, one can intelligently design the pore environment. However,	our 
+	of LC monomers, one could 
+        %MRS: suggest can->could.
+intelligently design the pore environment. However, our 
 	current understanding of the nanoscopic pore structure is not yet adequate for us to
@@
 	%BJC: following is quite similar to the abstract
-	In this paper, we used molecular dynamics (MD) simulations in order to model an
-	experimentally characterized LLC polymer membrane and learn about its atomistic
-	structure in detail. We simulated XRD patterns from the MD simulation trajectories
+	In this paper, we used molecular dynamics (MD) simulations to model an
+	experimentally characterized LLC polymer membrane and learn about its detailed atomistic
+	structure. We simulated XRD patterns from the MD simulation trajectories
 	for comparison to experimental 2D wide-angle X-ray scattering (WAXS) and 1D 
-	small-angle X-ray scattering patterns. While trying to match our simulated patterns
-	to experimental patterns, we found that 5 columns of stacked LLC monomers are 
-	likely to pack around the hydrophilic core of each pore. We learned that these 
+	small-angle X-ray scattering patterns. We found that 5 columns of stacked LLC monomers are 
+	likely to pack around the hydrophilic core of each pore. These 
 	columns likely move independently of each other	over time scales that we can not
-	simulate. We also found that some of the structure previously attributed to monomer
+	simulate. Some of the structure previously attributed to monomer
 	tail tilt is likely instead due to ordered tail packing. Although the system studied
-	has been reported as ``dry", we show that small amounts	of water are necessary to 
+	has been reported as ``dry'', small amounts of water appear necessary to 
 	fully reproduce all features from the experimental 2D-WAXS pattern due to asymmetries
-	introduced by hydrogen bonds between the LC monomer head groups and water molecules.
-	Finally, we explored the composition and structure of the nanopores and reveal that
-	there exists a composition gradient rather than an abrupt partition between the 
+	introduced by hydrogen bonds between the LLC monomer head groups and water molecules.
+	Finally, we explored the composition and structure of the nanopores, showing there is 
+        composition gradient rather than an abrupt partition between the 
 	hydrophilic and hydrophobic regions. The clearer picture of the nanoscopic structure
@@
 
-	%BJC: subject to change
+	%MRS: don't need phone numbers.
 	\noindent Some suggestions for reviewers are:
@@
 		properties of the same inverted hexagonal phase LLC membrane studied in our 
-		work (University of Pennsylvania, 215-573-3608, 
+		work (University of Pennsylvania, 
 		\href{mailto:cosuji@seas.upenn.edu}{cosuji@seas.upenn.edu}).
+                %MRS: osuji might be a conflict of interest due to supervising Xunda recently plus joint grants with Gin, but I don't know for sure. Can leave him on for now.
 		\item Menachem Elimelech is a leader in the development of membrane technologies
-		for	water desalination and water reuse (Yale University, 203-432-2789, 
+		for	water desalination and water reuse (Yale University, 
 		\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).
@@
 		of liquid crystals into ordered nanostructures, including the type studied
-		in our work. (Univeristy of Wisconsin Madison, 608-262-0258, 
-		\href{mailto:yethiraj@chem.wisc.edu}{yethiraj@chem.wisc.edu})  % questionable due to related self-assembly research.
+		in our work. (University of Wisconsin Madison, 
+		\href{mailto:yethiraj@chem.wisc.edu}{yethiraj@chem.wisc.edu})  % questionable due to related self-assembly research. MRS: I looked over his recent papers, and I think will be OK.
 	\end{enumerate}
@@
 	% Jeff McCutcheon - My undergrad advisor. Advised by Elimelech for his PhD.
-	% Benoit Roux?
-	% Eric Jankowski - Boise State, met at FOMMS. One of his students works with simulated XRD patterns. I actually think this is a much better idea than Yethiraj
+        % conflicts of interest for the first two with the authors.
+	% Benoit Roux? - No, too busy and critical.
+	% Eric Jankowski - Boise State, met at FOMMS.
+One of his students works with simulated XRD patterns.
+I actually think this is a much better idea than Yethiraj.
+Good choice, can put as well as Yethiraj.
 
@@
     %BJC: so many authors, it runs off the page. Can just say "Sincerely, the authors" or list names on single line separated by commas. 
-    and co-authors
-    %\noindent Joseph Yelk \\
-    %\noindent Matthew A. Glaser
-    %\noindent Douglas L. Gin \\
-    %\noindent Xunda Feng \\
+    %Now there is space.
+    \noindent Joseph Yelk \\
+    \noindent Matthew A. Glaser
+    \noindent Douglas L. Gin \\
+    \noindent Xunda Feng \\
 
 \end{document}
+
+% LocalWords:  BJC

### 2018-09-27 Ben_Manuscripts/structure_paper/Draft.tex
Draft revisions
half of a read-through done

@@
 %MRS5: could be punchier. I will keep thinking.  
-\title{Understanding the nanoscale structure of inverted hexagonal phase lyotropic liquid crystal polymer membranes}
+\title{Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
 \author{Benjamin J. Coscia}
@@
   polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
-  domains, created by the "dry" monomer Na-GA3C11, using a magnetic field
+  domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
   with subsequent cross-linking to lock the structure in
@@
 	create columns with short range order then assemble into pores with  
-	hydrophilic head groups (blue) face towards the pore center. (e) The 
+	hydrophilic head groups (blue) facing towards the pore center. (e) The 
 	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
@@
 
+  %BJC16: This figure could probably be cut or moved to supporting info
   \begin{figure}[!htb]
@@
 	R-double has been previously interpreted as 2\textsubscript{1} helical ordering of aromatic
-	rings along the $z$ axis\cite{feng_scalable_2014}.
+	rings along the $z$-axis\cite{feng_scalable_2014}.
         %meaning if one traces the 
@@
 	\AA$^{-1}$ marks the third major reflection of interest. The real space
-	separation corresponds to 4.5 \AA~ which is characteristic of the average
+	separation corresponds to 4.5 \AA~which is characteristic of the average
 	spacing between packed alkane chains \cite{mcintosh_organization_1980}. We will
@@
 	is characterized by reflections along the equatorial axis defined by $q_z$ = 0.
-	The spacing between dots is indicative of the hexagonal symmetry of the 
-	packed pores, and the location of the leading peak (closest to $q_r$ = 0)
-	is related to the distance between pores. We observe the same information
-	with higher resolution by looking at the same system's 1D-SAXS pattern 
-	(Fig.~\ref{fig:SAXS}).
-
+	The spacing between dots is indicative of the hexagonal symmetry of the packed
+	pores. We observe the same information with higher resolution by looking at the
+	same system's 1D-SAXS pattern (Fig.~\ref{fig:SAXS}). The location of the
+	leading SAXS peak (closest to $q_r$ = 0) is related to the distance between
+	pores.
   \end{enumerate}
@@
 
- 	Authors often describe this and similar systems as being made up of layers. A simple
+ 	Authors often describe this and similar systems as being made up of stacked monomer layers. A simple
  	molecular simulation study of a similar molecule suggested that there are 4 monomers
@@
  	In the system we are studying, there are long-range 2D correlations in the 
- 	hexagonal array of pores (xy plane) and short range z-direction correlations between 
+ 	hexagonal array of pores (xy plane) and short range $z$-direction correlations within 
         stacked columns of monomers. In this study, we use atomistic molecular modeling
@@
   number of columns per pore. We built systems in the sandwiched and parallel
-  displaced configurations with 4, 5, 6, 7 and 8 monomers per layer.
+  displaced configurations with 4, 5, 6, 7 and 8 columns per pore.
 
@@
   We measured the one dimensional pair distribution function, $g(z)$, between centers 
-  of masses (COM) of aromatic head group rings along the z-axis (perpendicular to
+  of masses (COM) of aromatic head group rings along the $z$-axis (perpendicular to
   the membrane plane). We averaged all 1D $z$-directional slices of the full 3D 
@@
   equally spaced points surrounding the pore center. This method for calculating 
-  quenched order inherently includes thermal disorder.
+  quenched disorder inherently includes thermal disorder.
 
@@
   of trajectories consisting of 1000 independent simple system configurations 
-  generated with point scatterer placement based on the quenched order seen in
+  generated with point scatterer placement based on the quenched disorder seen in
   atomistic simulations. The quenched disorder is greater in  magnitude than thermal 
@@
   systems with monomers initially spaced 5 \AA~apart vertically (see Section~\ref{S-section:initial_pore_spacing}
-  of the Supporting Information for more details on sensitivity to initial layer spacing). 
+  of the Supporting Information for more details on sensitivity to initial monomer spacing). 
   We considered the pore-to-pore spacing to be equilibrated as defined in Section~\ref{method:equil_time}.
@@
   be characterized as being in a more ordered basin, and any system where $\mathit{d}=5.0$ \AA~can
-  be characterized as a more the disordered basin. Generally, when monomers are started further 
+  be characterized as begin in a more disordered basin. Generally, when monomers are started further 
   apart, they stay further apart than systems where monomers are started closer together 
-  (see Table~\ref{table:correlation_length}). Because of the extra space between stacked 
-  monomers, monomer head groups have more rotational freedom. We quantified the ordering of
+  (see Table~\ref{table:correlation_length}). Extra space between stacked 
+  monomers give the monomer head groups more rotational freedom. We quantified the ordering of
   the head groups using the nematic order parameter (see Section S-\ref{S-method:nematic_order}
@@
 	  in any simulated patterns, and thus has no measurable intensity. In terms of 
-	  the locations of the reflections, R-pores, R-alkanes and R-spots appear at $q$
-	  values that close to experiment, while R-$\pi$ appears at a significantly lower
-	  $q$ value than experiment.\label{table:relative_intensities_300K}}
+	  the locations of the reflections, R-pores, R-alkanes and R-spots appear at $|\mathbf{q}|$
+	  values that are close to experiment, while R-$\pi$ appears at a significantly lower
+	  $|\mathbf{q}|$ value than experiment.\label{table:relative_intensities_300K}}
   \end{table}
@@
 
+  \section*{Supporting Information}
+
+  Detailed explanations and expansions upon the results and procedures mentioned in 
+  the main text are described in the Supporting Information. This information is 
+  available free of charge via the Internet at http://pubs.acs.org.
+
   \section*{Acknowledgements}
@@
   for useful discussions that enhanced our understanding of these LC membrane systems.
-
-  \section*{Supporting Information}
-
-  Detailed explanations and expansions upon the results and procedures mentioned in 
-  the main text are described in the Supporting Information. This information is 
-  available free of charge via the Internet at http://pubs.acs.org.
 

### 2018-09-28 Ben_Manuscripts/structure_paper/cover_letter.tex
Revisions

@@
 
-	%MRS: I shortened this a bit and made it more direct; was a bit long.
 	\noindent Dear Editors,\\
-	%MRS: don't need to put they are graduate students or postdics. 
+
+	%MRS: don't need to put they are graduate students or postdocs.
+	%BJC: but it says to do that in the author's guide 
 	We are submitting ``Understanding the Nanoscale Structure of Inverted Hexagonal 
-	Phase Lyotropic Liquid Crystal Polymer Membranes'' by Benjamin J. Coscia, Joseph Yelk, Matthew A. Glaser, Douglas
-	L. Gin, Xunda Feng, and Michael R. Shirts, for
+	Phase Lyotropic Liquid Crystal Polymer Membranes'' by Benjamin J. Coscia, Joseph
+	Yelk, Matthew A. Glaser, Douglas L. Gin, Xunda Feng, and Michael R. Shirts, for
 	consideration for publication as an Article in the Journal of Physical Chemistry
@@
 
-        %MRS: maybe ``examines'' instead of studies. 
 	This article examines the atomistic structure of an inverted hexagonal phase 
@@
 	separations of small solutes. By tuning the shape, size and chemical functionality
-	of LC monomers, one could 
-        %MRS: suggest can->could.
-intelligently design the pore environment. However, our 
+	of LC monomers, one could intelligently design the pore environment. However, our 
 	current understanding of the nanoscopic pore structure is not yet adequate for us to
@@
 
-	%BJC: following is quite similar to the abstract
 	In this paper, we used molecular dynamics (MD) simulations to model an
-	experimentally characterized LLC polymer membrane and learn about its detailed atomistic
-	structure. We simulated XRD patterns from the MD simulation trajectories
+	experimentally characterized LLC polymer membrane and learn about its detailed
+	atomistic structure. We simulated XRD patterns from the MD simulation trajectories
 	for comparison to experimental 2D wide-angle X-ray scattering (WAXS) and 1D 
-	small-angle X-ray scattering patterns. We found that 5 columns of stacked LLC monomers are 
-	likely to pack around the hydrophilic core of each pore. These 
+	small-angle X-ray scattering patterns. We found that 5 columns of stacked LLC 
+	monomers are likely to pack around the hydrophilic core of each pore. These 
 	columns likely move independently of each other	over time scales that we can not
-	simulate. Some of the structure previously attributed to monomer
-	tail tilt is likely instead due to ordered tail packing. Although the system studied
-	has been reported as ``dry'', small amounts of water appear necessary to 
-	fully reproduce all features from the experimental 2D-WAXS pattern due to asymmetries
-	introduced by hydrogen bonds between the LLC monomer head groups and water molecules.
+	simulate. Some of the structure previously attributed to monomer tail tilt is 
+	likely instead due to ordered tail packing. Although the system studied	has been
+	reported as ``dry'', small amounts of water appear necessary to fully reproduce 
+	all features from the experimental 2D-WAXS pattern due to asymmetries introduced 
+	by hydrogen bonds between the LLC monomer head groups and water molecules. 
 	Finally, we explored the composition and structure of the nanopores, showing there is 
-        composition gradient rather than an abrupt partition between the 
-	hydrophilic and hydrophobic regions. The clearer picture of the nanoscopic structure
+	composition gradient rather than an abrupt partition between the hydrophilic and
+	hydrophobic regions. The clearer picture of the nanoscopic structure
 	of these membranes provided in this study will enable a better understanding of the
@@
 	%MRS: don't need phone numbers.
+	%BJC: says to do that in author's guide
 	\noindent Some suggestions for reviewers are:
@@
 		\href{mailto:cosuji@seas.upenn.edu}{cosuji@seas.upenn.edu}).
-                %MRS: osuji might be a conflict of interest due to supervising Xunda recently plus joint grants with Gin, but I don't know for sure. Can leave him on for now.
+        % MRS: osuji might be a conflict of interest due to supervising Xunda recently plus
+        % joint grants with Gin, but I don't know for sure. Can leave him on for now.
 		\item Menachem Elimelech is a leader in the development of membrane technologies
@@
 		\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).
-		\item Arun Yethiraj has studied molecular simulations of the self-assembly
-		of liquid crystals into ordered nanostructures, including the type studied
-		in our work. (University of Wisconsin Madison, 
-		\href{mailto:yethiraj@chem.wisc.edu}{yethiraj@chem.wisc.edu})  % questionable due to related self-assembly research. MRS: I looked over his recent papers, and I think will be OK.
+		\item Eric Jankowski has experience modeling soft materials using molecular dynamics
+		including work done simulating structure factors from simulations, much like
+		the techniques we use in our work (Boise State University
+		\href{mailto:ericjankowski@boisestate.edu}{ericjankowski@boisestate.edu})
+
+		% BJC: Yethiraj is an editor so can't use him
+%		\item Arun Yethiraj has studied molecular simulations of the self-assembly
+%		of liquid crystals into ordered nanostructures, including the type studied
+%		in our work. (University of Wisconsin Madison, 
+%		\href{mailto:yethiraj@chem.wisc.edu}{yethiraj@chem.wisc.edu})  
+		% questionable due to related self-assembly research. 
+		% MRS: I looked over his recent papers, and I think will be OK.
 	\end{enumerate}
@@
     \noindent Benjamin J. Coscia \\
-    %BJC: so many authors, it runs off the page. Can just say "Sincerely, the authors" or list names on single line separated by commas. 
-    %Now there is space.
     \noindent Joseph Yelk \\

### 2018-09-28 Ben_Manuscripts/structure_paper/Draft.tex
Revisions
revisions

@@
 		\centering
-		\includegraphics[width=\textwidth]{NaGA3C11.eps}
+		\includegraphics[width=\textwidth]{NaGA3C11.pdf}
 		\caption{}~\label{fig:monomer}
@@
   Wang et al. highlighted the shortcoming of some of the most popular protein
-  force field in predicting the temperature dependence of protein structural
+  force fields in predicting the temperature dependence of protein structural
   ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
@@
   compared to the experimental structure at 300 K. We found that lowering the
-  temperature indeed better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
+  temperature better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
   suggesting that our `effective' temperature might indeed be too high,
@@
   the R-spots reflection is packing of the tails in a hexagonal array.
-  First, we demonstrate R-spots comes primarily from the tails, by
+  First, we demonstrated that R-spots comes primarily from the tails by
   removing all non-tail atoms from the trajectory and simulating the
-  XRD diffraction pattern with the remaining atoms, which preserves
+  XRD pattern with the remaining atoms, which preserves
   R-spots (Figure~\ref{fig:tails_rzplot}). Next, we plotted the center
@@
       simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
-      Since the tails stay relatively flat, we plotted the center of mass of the first
+      Since the tails stay relatively flat, we plotted the COM of the first
       four carbon atoms of each tail originating from the head groups (for example,
-      green colored centroids in the plot surround the red centroid in hexagonal fashion).
+      green colored COMs in the plot surround the red COM in hexagonal fashion).
       Visually, the packing looks hexagonal. (e) We hypothesize
@@
       mass and its nearest neighbor center of masses for the equilibrated 
-      sandwiched configuration simulated at 280K. Peaks appear in the distribution at 
+      sandwiched configuration simulated at 280 K. Peaks appear in the distribution at 
       $-60\degree$, $0\degree$ and $60\degree$. (f) The Fourier transform of a hexagonally
@@
   does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
-  it more energetically favorable for the monomers to stack closer together ~\cite{wang_development_2004}.
+  it more energetically favorable for the monomers to stack closer together~\cite{wang_development_2004}.
   It is also possible that the tails prevent close stacking of monomer head groups
@@
   throughout $g(z)$ in both cases (See
-  Figure~S-\ref{S-fig:z_correlation_overlay}).
+  Figure~S-\ref{S-fig:z_correlation_overlay} in the Supporting Information).
 
@@
   Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
-  Experiment         & --                 &    3.70                    & 10 $\pm$ 1               \\
+  Experiment         & --                 &    3.70                    & 9 $\pm$ 1               \\
   \bottomrule
@@
 	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
-	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
+	  to 3.2. The edges of the peak are beginning to smooth out, but sharp peaks
 	  still exist. (c) When columns are completely independent, $f$ = 1, the
-	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
+	  intensity of R-$\pi$ decreases 8-fold to 2.1 and the cross-section is
           relatively smooth.}\label{fig:column_displacement}
@@
   3D correlation function. When we include all $z$-slices in $g(z)$ for our
-  system, rather than restricting it to those $z$-slices within 2.1 \AA of the
+  system, rather than restricting it to those $z$-slices within 2.1 \AA~of the
   center of the correlation function (Section~\ref{section:correlation_length}),
   the function shows oscillatory behavior and the correlation length
-  nearly triples to 12.4 $\pm$ 0.7 \AA. (Figure~\ref{fig:z_correlation_fullbox}).
+  nearly triples to 12.4 $\pm$ 0.7 \AA~(Figure~\ref{fig:z_correlation_fullbox}).
   Since all columns in our initial configuration are started at the same
@@
   \caption{Increasing the amount of disorder in the $xy$ plane decreases the
-	  FWHM of the $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and
+	  FWHM of the $q_r$ cross-section of R-$\pi$. When we cut the amount of $r$ and
 	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
@@
   \caption{(a) The standard deviation of the distribution of quenched disorder
-  from the first 5 ns of the main ordered parallel displaced system studied in
+  from the first 5 ns of the main (400 ns) ordered parallel displaced system studied in
   this paper (black dashed line) is in agreement with the distribution of quenched disorder 
@@
   are necessarily 0 so they are not plotted. (c) The radial densities of tail
-  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
-  main system simulation trajectory (black lines) and from the ensemble of 
-  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
+  atoms, head group atoms and sodium atoms, as a function of distance from the pore center,
+  calculated from the first 5 ns of the main system simulation trajectory (black lines) 
+  and from the ensemble of trajectories (purple) look qualitatively similar. The 95 \%
+  confidence interval generated based on the ensemble of simulations is shaded in purple.}\label{fig:ensemble_stds}
   \end{figure}
@@
   of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
-  ordering in the $z$-direction in addition to high degrees of correlation 
+  ordering in the $z$-direction in addition to a high degree of correlation 
   between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
@@
   parallel displaced, but their displacement is likely only slightly shifted, on 
-  the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
+  the $xy$ plane, from the COM of their vertically adjacent neighbors 
   (see Figure~S-\ref{S-fig:between_pd} of the Supporting Information). In this way,
@@
   result in the appearance of R-double below, and we can speculate which makes
-  the most physical sense. It appears that we cannot achieve a long-term stable
-  system that exhibits R-double without the inclusion of small amounts of water
-  in the pores.
+  the most physical sense.
+
+% Following is in previous paragraph
+%It appears that we cannot achieve a long-term stable
+%  system that exhibits R-double without the inclusion of small amounts of water
+%  in the pores.
 
@@
   barrier that prevents rotation of carboxylate groups attached to phenyl rings
-  since the group extends the system's $\pi$ conjugation ~\cite{carey_organic_2011} (see Figure
-  S-\ref{S-fig:carboxylate_dihedral_rb} of the Supporting Information), which is significant even considering
-  possible overestimates of the barrier height in the classical force field. 
+  since the group extends the system's $\pi$
+  conjugation~\cite{carey_organic_2011}, which is significant even considering
+  possible overestimates of the barrier height in the classical force field (see
+  Figure S-\ref{S-fig:carboxylate_dihedral_rb} of the Supporting Information). 
 %  
@@
   Another way to produce R-double is if we rotate monomers with respect to
-  vertically adjacent monomers. In this configuration, the LLC monomers are rotated so
-  that the vector created by the bond extending from the carboxylate carbon to
-  the phenyl ring is oriented $\pm 15 \degree$ with respect to the vector
-  extending from the head group COM to the pore center (Figure
+  vertically adjacent monomers on the $xy$ plane. In this configuration, the LLC
+  monomers are rotated so that the vector created by the bond extending from the
+  carboxylate carbon to the phenyl ring is oriented $\pm 15 \degree$ with respect
+  to the vector extending from the head group COM to the pore center (Figure
   ~\ref{fig:rotated_monomers_rzplot_norestraints}). Every other monomer layer is
@@
   may be the most favorable way for them to pack. This configuration is only
-  stable for a few nanoseconds but R-double quickly fades. 
+  stable for a few nanoseconds before R-double quickly fades. 
   %MRS12: seems like unnecssary speculation below, since there are a lot of cancelling affects. 
@@
   are applied to heavy atoms of the phenyl rings.  Additionally, there is little
-  evidence from QM studies of stacked $\pi-\pi$ systems that such uneven stacking
+  evidence from QM studies of stacked $\pi-\pi$ systems that suggest uneven stacking
   could be energetically stable.~\cite{tauer_beyond_2005}
@@
 	  adjacent monomers (top), R-double is visible while the heavy atoms of the head
-	  groups are held in place with position restraints (middle). Again, R-double
-	  fades once the position restraints are released. (b) When monomers are
+	  groups are held in place with position restraints (middle). R-double
+	  fades once the position restraints are released (bottom). (b) When monomers are
 	  non-uniformly spaced (top), R-double appears if all heavy atoms of the head
-	  groups are held in place with position restraints (middle). R-double quickly
+	  groups are held in place with position restraints (middle). Again, R-double quickly
 	  fades once the position restraints are released (bottom). (c) When we add 1
@@
   monomers' hydroscopicity. Anecdotal evidence from other researchers suggests
-  that membranes are less likely to assemble under completely dry
+  that these membranes are less likely to assemble under completely dry
   conditions, supporting the idea %~\cite{personal_communication_with_mike_mcgrath} <- BJC16: what do I do with this?
@@
   $10^{-14}~m^2/s$. However, since on this timescale, no monomers move
+%BJC16: is it an overestimate or underestimate? 
   a full `level` above or below, this may be an overestimate. This slow speed is
@@
   function plateau's near a value of -0.2 which indicates that the tails are starting in 
-  an unfavorable configuration. We implemented distance restraints between the centers of 
-  mass of monomer head groups to preserve the hexagonal phase, then raised the temperature 
+  an unfavorable configuration. We implemented distance restraints between the COMs 
+  of monomer head groups to preserve the hexagonal phase, then raised the temperature 
   of the equilibrated 300 K ordered basin sandwiched system to 500 K. We witnessed 
@@
   monomers were either involved in a cross-linking reaction or were terminated 
-  (see Section S-\ref{S-section:xlink} of the Supporting Information)
+  (see Section S-\ref{S-section:xlink} of the Supporting Information
   for further details of the cross-linking algorithm). We allowed the cross-linked
@@
   predicted. We find that R-spots is likely due to ordered alkane chain packing.
-  R-$\pi$ appears at lower q values than experiment because monomer stack too far
+  R-$\pi$ appears at lower $q$ values than experiment because monomer stack too far
   apart, and its intensity is far too high, likely because our initial

### 2018-09-28 Ben_Manuscripts/structure_paper/Draft.tex
Revisions, citations and new figures

--- 2018-09-27 Ben_Manuscripts/structure_paper/Draft.tex
@@
   correlation length varies as the inverse of the full width at half maximum
-  (FWHM) of the $q_z$ cross-section of R-$\pi$.  Using this technique, we
-  calculated the correlation length of the experimental system to be 9.0 \AA. As
-  scatterers become less correlated, we expect that R-$\pi$ will broaden.
+  (FWHM) of the $q_z$ cross-section of R-$\pi$~\cite{young_highly_2013-1}. Using
+  this technique, we calculated the correlation length of the experimental 
+  system to be 9.0 \AA. As scatterers become less correlated, we expect that
+  R-$\pi$ will broaden.
 
@@
   easily simulate such as finite size crystalline domains and instrumental % reference needed
-  resolution.  In our simulated XRD patterns, the system size imposes limitations
+  resolution~\cite{girolami_x-ray_2016}. In our simulated XRD patterns, 
+  the system size imposes limitations
   on the resolution, which makes it difficult to reliably fit peaks. This is
@@
 
-  %BJC15: will not waste much time formatting until we converge on a figure 
   \begin{figure}[!htb]

### 2018-09-28 Ben_Manuscripts/structure_paper/supporting_information.tex
Revisions, citations and new figures

@@
 
+  \section{2D Small Angle X-ray Scattering Data}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{2DSAXS_axes.png}
+  \caption{Two dimensional small angle X-ray scattering experiments show
+  reflections along the $q_r$ axis at $q_z$=0. The spacing between the reflections
+  is characteristic of a hexagonal phase and is directly related to the distance
+  between pores. The reflections are arced because the pores are not perfectly
+  aligned. A perfectly aligned system would show dots at each peak location. An
+  isotropically aligned system would show concentric rings about the origin which
+  pass through each peak location. The d\textsubscript{100} and d\textsubscript{110} 
+  peaks (the first two pairs of reflections from origin located at $|\mathbf{q}| 
+  \approx 0.18~\AA^{-1}$ and $|\mathbf{q}| \approx 0.31~\AA^{-1}$) are not visible
+  in the 2D WAXS pattern. The edges of the d\textsubscript{200} reflection (the third
+  pair of reflections located at $|\mathbf{q}| \approx 0.36~\AA^{-1}$) are slightly
+  visible in the 2D WAXS pattern, so we used them to approximate the experimental
+  intensity of R-pores.}\label{fig:2DSAXS}
+  \end{figure}
+
+  \newpage
+
   \section{Component radial density functions}\label{section:radial_density}
@@
 %  \end{figure}
-
-  \section{2D Small Angle X-ray Scattering Data}
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=0.5\textwidth]{2DSAXS_axes.png}
-  \caption{Two dimensional small angle X-ray scattering experiments show
-  reflections along the $q_r$ axis at $q_z$=0. The spacing between the reflections
-  is characteristic of a hexagonal phase and is directly related to the distance
-  between pores. The reflections are arced because the pores are not perfectly
-  aligned. A perfectly aligned system would show dots at each peak location. An
-  isotropically aligned system would show concentric rings about the origin which
-  pass through each peak location. The d\textsubscript{100} and d\textsubscript{110} 
-  peaks (the first two pairs of reflections from origin located at $|\mathbf{q}| 
-  \approx 0.18~\AA^{-1}$ and $|\mathbf{q}| \approx 0.31~\AA^{-1}$) are not visible
-  in the 2D WAXS pattern. The edges of the d\textsubscript{200} reflection (the third
-  pair of reflections located at $|\mathbf{q}| \approx 0.36~\AA^{-1}$) are slightly
-  visible in the 2D WAXS pattern, so we used them to approximate the experimental
-  intensity of R-pores.}\label{fig:2DSAXS}
-  \end{figure}
 
@@
 
+  \section{Ensemble of ordered sandwiched configurations}
+
+  Here we show the results of the same analysis shown in Figures~\ref{M-fig:ensemble_XRD} 
+  and~\ref{M-fig:full_ensemble_distributions} of the main text for the 
+  ordered sandwiched ensemble of configurations.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.pdf}
+  \caption{Distributions of deviations from ideal positions generated with data
+  from all independent simulations}\label{fig:offset_ensemble_pooled}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{sandwiched_ecdfs.pdf}
+  \caption{Empirical cumulative distribution functions generated from (a) and
+  from simulation ensembles.}\label{fig:offset_ecdfs}
+  \end{subfigure}
+  \caption{(a) The distributions of the head group COM deviations
+  from their idealized positions generated using pooled data from all
+  frames of each independent configuration are symmetric, implying that 
+  there is equal probability for a head group to displace in the positive
+  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
+  given head group is displaced randomly upon quenching. The ECDF generated from
+  the pooled distributions (black) in (a) agree with the means of the 
+  ECDFs generated from each COM (red). The red error bars are larger than
+  the black error bars since there is a wider distribution of mean COM
+  deviations than the mean deviations of distributions sampled from the full
+  distribution.}\label{fig:full_ensemble_distributions}
+  \end{figure}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.pdf}
+  \caption{}\label{fig:offset_ensemble_stds}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{sandwiched_ensemble_means.pdf}
+  \caption{}\label{fig:offset_ensemble_means}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{sandwiched_ensemble_regional_density.pdf}
+  \caption{}\label{fig:offset_ensemble_regional_density}
+  \end{subfigure}
+  \caption{(a) The standard deviation of the distribution of quenched disorder
+  from the first 5 ns of the main ordered sandwiched system studied in
+  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
+  standard deviations calculated from the ensemble of simulations (histogram). 
+  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
+  system trajectory (black dashed line) is in agreement with the distribution of mean values
+  calculated from each simulation in the ensemble (histogram). The mean values of $z$
+  are necessarily 0 so they are not plotted. (c) The radial densities of tail
+  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
+  main system simulation trajectory (black lines) and from the ensemble of 
+  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
+  \end{figure}
+
+  \clearpage
+
   \section{Carboxylate Dihedrals}

### 2018-10-05 Ben_Manuscripts/structure_paper/supporting_information.tex
Added links to code

@@
 \externaldocument[M-]{Draft}
-\title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}
+\title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
+\author{Benjamin J. Coscia \and Jospeh Yelk \and Matthew A. Glaser \and Douglas L. Gin \and Xunda Feng \and Michael R. Shirts}
+\date{}
 

### 2018-10-05 Ben_Manuscripts/structure_paper/cover_letter.tex
Updates

@@
 
-	%MRS: don't need to put they are graduate students or postdocs.
-	%BJC: but it says to do that in the author's guide 
 	We are submitting ``Understanding the Nanoscale Structure of Inverted Hexagonal 
@@
 
-	%MRS: don't need phone numbers.
-	%BJC: says to do that in author's guide
+	%BJC: included phone numbers because it asked to do so in author's guide.
 	\noindent Some suggestions for reviewers are:
 	\begin{enumerate}
-		\item Chinedum Osuji has published work related to the synthesis and physical
-		properties of the same inverted hexagonal phase LLC membrane studied in our 
-		work (University of Pennsylvania, 
-		\href{mailto:cosuji@seas.upenn.edu}{cosuji@seas.upenn.edu}).
-        % MRS: osuji might be a conflict of interest due to supervising Xunda recently plus
-        % joint grants with Gin, but I don't know for sure. Can leave him on for now.
+
 		\item Menachem Elimelech is a leader in the development of membrane technologies
-		for	water desalination and water reuse (Yale University, 
+		for	water desalination and water reuse (Yale University, 203-432-2789,
 		\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).
+
+		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
+		and various	nanostructured materials (Northeastern Univerity, 617-373-8619 	
+		\href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})
+
 		\item Eric Jankowski has experience modeling soft materials using molecular dynamics
 		including work done simulating structure factors from simulations, much like
-		the techniques we use in our work (Boise State University
+		the techniques we use in our work (Boise State University, 208-426-5681,
 		\href{mailto:ericjankowski@boisestate.edu}{ericjankowski@boisestate.edu})
 
-		% BJC: Yethiraj is an editor so can't use him
-%		\item Arun Yethiraj has studied molecular simulations of the self-assembly
-%		of liquid crystals into ordered nanostructures, including the type studied
-%		in our work. (University of Wisconsin Madison, 
-%		\href{mailto:yethiraj@chem.wisc.edu}{yethiraj@chem.wisc.edu})  
-		% questionable due to related self-assembly research. 
-		% MRS: I looked over his recent papers, and I think will be OK.
 	\end{enumerate}
-
-	%BJC: Other reviewer ideas:
-	% Jason Bara - University of Alabama -- former member of Gin/Noble group who worked on
-	% bicontinuous cubic phase at one point. He helped me figure out how to print the 3D models
-	% Jeff McCutcheon - My undergrad advisor. Advised by Elimelech for his PhD.
-        % conflicts of interest for the first two with the authors.
-	% Benoit Roux? - No, too busy and critical.
-	% Eric Jankowski - Boise State, met at FOMMS.
-One of his students works with simulated XRD patterns.
-I actually think this is a much better idea than Yethiraj.
-Good choice, can put as well as Yethiraj.
 

### 2018-10-07 Ben_Manuscripts/structure_paper/Draft.tex
Added links to code
Updates
comments.

@@
 
-%MRS5: could be punchier. I will keep thinking.  
 \title{Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
@@
   of self-assembled lyotropic liquid crystals (LLCs) are a promising class of materials
-  for selective separations. In this work, we investigated an experimentally
+  for selective separations. In this work, we investigate an experimentally
   characterized LLC polymer membrane using atomistic molecular modeling. In particular,
-  we compared simulated X-ray diffraction (XRD) patterns with experimental XRD data
+  we compare simulated X-ray diffraction (XRD) patterns with experimental XRD data
   to quantify and understand the differences between simulation and experiment.
-  We found that the nanopores are likely composed of 5 columns of stacked LLC monomers
-  which surround each hydrophilic core. We learned that these columns likely 
-  move independently of each other over time scales that we can not simulate.
-  We also found that some of the structure previously attributed to monomer tail 
+  We find that the nanopores are likely composed of 5 columns of stacked LLC monomers
+  which surround each hydrophilic core. Evidence suggests that these columns likely 
+  move independently of each other over longer time scales than accessible via atomistic simulation.
+  We also find that WAXS structural features previously attributed to monomer tail 
   tilt is likely instead due to ordered tail packing. Although this system
   has been reported as dry, we show that small amounts of water are necessary
-  to fully reproduce all features from the experimental XRD pattern due to
+  to reproduce all features from the experimental XRD pattern due to
   asymmetries introduced by hydrogen bonds between the monomer head groups and
-  water molecules. Finally, we explored the composition and structure of the nanopores
+  water molecules. Finally, we explore the composition and structure of the nanopores
   and reveal that there exists a composition gradient rather than an abrupt
@@
   that the time scales of the dynamics are extremely long for this system, 
-  resulting in simulated structures that appear too ordered which requires
+  resulting in simulated structures that appear too ordered, thus requiring
   careful examination of the metastable states observed in order to draw any
@@
 
+  %MRSF: I changed the description of the ``demonstrating'', ``showing'' verbs to present tense.
+The experiments are past tense, but the ``showing'' is present tense, since it is occuring while the reader is reading (like in a presentation - you are showing as they listen).
   \end{abstract}
@@
 
-  More highly selective nanoporous membranes would be extremely useful in order
-  to perform complex aqueous separations with seawater and various sources of
-  wastewater. Sodium chloride and boron in seawater
-  \cite{fritzmann_state---art_2007}, and organic micropollutants found in
-  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are
-  examples of the diverse constituents of these water sources. By efficiently
+  More highly selective nanoporous membranes would be extremely useful 
+  %in order to perform 
+  in performing complex aqueous separations with seawater and various 
+  %sources 
+  types of
+  wastewater. 
+  For exaple, 
+  Sodium chloride and boron in seawater
+  \cite{fritzmann_state---art_2007} and organic micropollutants found in
+  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} represent just a few of the diverse contaminants 
+  of water sources. By efficiently
   separating contaminants from feed solutions with highly selective membranes,
@@
   needed for a given filtration process \cite{werber_materials_2016}, thus
-  lowering energy requirements. Additionally, one can extract valuable resources
+  lowering energy requirements. Additionally, one can also extract valuable resources
   from the feed streams. For example, flowback water produced during hydraulic
@@
 
+%MRSF: a few selelected edits above, but I think strikes the right balance.
 % More highly selective membranes would be extremely useful for both the
@@
   filtration processes that can be used to separate solutes on the order of 1 nm
-  in size and smaller, as well as ions. However the porous architecture of
-  commercially available membranes lack uniformity, which severely impacts their
+  in size and smaller, including 
+  %as well as 
+  %MRSF: this does seem to blend RO and NF together; is this correct, or are there important differences that should be outlined?
+  ions. However, the porous architecture of
+  commercially available RO and NF membranes lack uniformity, which severely impacts their
   selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
@@
   defects during manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
-  Molecular dynamics (MD) simulations of carbon nanotubes show promise
+  Molecular dynamics (MD) simulations of carbon nanotubes have shown promise
   \cite{humplik_nanostructured_2011}, but synthetic techniques are unable to
@@
   \cite{hata_water-assisted_2004,maruyama_growth_2005}. Consequently, there is a
-  need for a scalable nanostructured porous membrane.
+  need for new materials that could provide scalable nanostructured porous membranes.
 
@@
   Preliminary evidence has shown that cross-linked lyotropic liquid crystal
-  (LLC) membranes are scalable and may be capable of performing highly selective
+  (LLC) membranes can be produced at moderate scale and may be capable of performing highly selective
   separations. LLCs are amphiphilic molecules that have the ability to
@@
   (Q\textsubscript{I})
-  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
+  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
   and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
@@
   hexagonally packed LC domains of the H\textsubscript{II}-phase
-  generally form mutually unaligned domains,
-  which are detrimental to membrane permeability. This domain scale misalignment
+  generally form mutually unaligned domains, which 
+  %are detrimental to 
+  hurts
+  membrane permeability. This domain scale misalignment
   had inhibited further development of this technology, and research efforts
@@
   with subsequent cross-linking to lock the structure in
-  place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could
+  place\cite{feng_scalable_2014}. In 2016, Feng et al.~showed that one could
   also obtain the same result by confining the neat monomer between PDMS or glass
@@
 	\end{subfigure}
+        %MRSF: in the actual paper, there would only be room for about a half-page figure, max.  Can hyou reduce the especially the c/d/e sizes so that it fully fits in a half-page figure? 
 	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
@@
   nanostructure is not sufficient to be able to precisely design them for
-  specific separations. Dischinger et al. attempted to use an empirical model
+  specific separations. Dischinger et al.~attempted to use an empirical model
   that correlates the physiochemical properties of the counterion used in a 
@@
 	\end{subfigure}
+    %MRSF: will probably need smaller figures for the paper. 
     \caption{(a) Previous understanding of the pores are essentially speculations 
@@
   Col\textsubscript{h} phase is a simpler starting point. The system is not
-  assembled in aqueous phase which allowed us to simulate longer timescales, and
-  there exists detailed experimental characterization of the fully aligned state,
+  assembled in aqueous phase which allowed us to simulate longer timescales
+  by omitting the solvent in the simulations,
+  and there exists detailed experimental characterization of the fully aligned state,
   including 2D-WAXS patterns (Figure~\ref{fig:WAXS}) that are useful for 
@@
 	relative intensity.  Accordingly, we name these reflections R-spots. The
-	location of all spots is $\sim\,37^{\circ}$ from the $q_z$ axis in their
-	respective quadrants. In many liquid crystal systems one can explain the spots
-	as the product of alkane chains tilted with respect to the membrane
+	location of all spots is $\sim$$37^{\circ}$ from the $q_z$ axis in their
+	respective quadrants. In many liquid crystal systems, such spots are explaioned
+	as the result of alkane chains tilted with respect to the membrane
 	plane\cite{govind_simple_2001}.
 
-	\item \textit{R-pores}: The final feature corresponds to the spacing
+	\item \textit{R-pores}: The final significant feature corresponds to the spacing
 	and symmetry of the pore columns. The feature, which we named R-pores,
@@
 		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
-		from \citenum{feng_thin_2016}) The repeat spacing in the 1D-SAXS
+		from Ref.\citenum{feng_thin_2016}) The repeat spacing in the 1D-SAXS
 		scattering pattern is characteristic of hexagonal packing. The leading peak,
-		q*, represents the distance between the d\textsubscript{100} planes. Using this
-		distance, we know that the distance between pore centers is 4.12 nm.} 
+		q*, represents the distance between the d\textsubscript{100} planes, which translates 
+                into a distance between pore centers of 4.12 nm.} 
 	\label{fig:SWAXS}
@@
   configuration from the trajectory which we used for full system
-  construction (Figure~\ref{fig:build_procedure}a). See Section S-\ref{S-section:parameterization} 
-  of the Supporting Information for further detail of the parameterization process.
+  construction (Figure~\ref{fig:build_procedure}a). Section S-\ref{S-section:parameterization} 
+  of the Supporting Information provides further detail of the parameterization process.
 
@@
 
-  The timescale for self-assembly of monomers into the hexagonal phase is
+  The time scale for self-assembly of monomers into the hexagonal phase is
   unknown and likely outside of a reasonable length for an atomistic simulation,
-  calling for a more efficient way to build the system. Previous work has shown
-  a united-atom model self assemble into the H\textsubscript{II} phase
+  requiring a more efficient way to build the system. Previous work has shown
+  a united-atom model of LLC can self-assemble into the H\textsubscript{II} phase
   configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
@@
   Supporting Information). 
-  To bypass the slow self-assembly process, we used Python scripts to assemble monomers
+  To bypass the slow self-assembly process, we used a variety of automated procedures 
+  %MRSF: code language is not as important
+  %Python scripts 
+  to assemble monomers
   into a structure close to one of a number of hypothesized equilibrium configurations
   (Figure~\ref{fig:build_procedure}).
+  %MRSF: where's the reference for the build scripts repository?
   %MRS13: Would be nice to say we put the scripts on GitHub.  Additional details about which scripts can be in supporting.
@@
   \end{subfigure}
+  %MRSF: I think this can be put in Supporting Information (we will get pushback to make this paper shorter, this is a good candidate)
   \caption{(a) We parameterized a single monomer and annealed it to produce a low-energy
@@
   When constructing an initial configuration, there are a number of variables
-  which require careful consideration while placing monomers. The equilibrium
-  configuration is sensitive to some while insensitive to others. We find the starting
+  which require careful consideration while placing monomers. We find that the equilibrium
+  configuration is sensitive to some while insensitive to others. For example, we find the starting
   pore radius, defined as the distance of a chosen head group carbon from the
   pore's central axis, does not influence the equilibrium structure if one chooses
-  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
-  configurations. The initial distance between pores, within a wide range, also has 
+  a reasonable value. The initial distance between pores, within a wide range, also has 
   little effect on the equilibrated structure. However, one should not start them
-  too close or there will be high energy repulsions during early equilibration. We 
-  chose an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
-  of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
+  too close or there will be high energy repulsions during early equilibration. We chose a pore radius of 0.5 nm and an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
+  of 4.12 nm for our initial configurations. A sensitivity analysis of both parameters is presented in the 
   Supporting Information, Section S-\ref{S-section:initial_config_dependence}. The 
@@
   to be replicated between experiment and simulation, as atomistic alkane
-  parameters are relatively well studied. Other features are dependent on system
+  force field parameters are relatively well-studied. Other features are dependent on system
   ordering which is likely to have some dependence on initial configuration.  We
@@
   $I_{avg}$ and divided all intensities by this value. In this way, the average
-  intensity of R-alkanes was equal to 1. When calculating $I_{avg}$, we excluded
-  intensities within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$,
+  intensity of R-alkanes was set equal to 1. When calculating $I_{avg}$, we excluded
+  intensities within $\pm$30\degree~of the meridional axis defined by $q_r=0$,
   since the simulated patterns differ from experiment in those regions in all
@@
   We calculated the radius as the sum of the longest C-C distance within a phenyl 
-  ring (2.8~\AA) and two times the carbon atom electronic radius (0.7~\AA)
-  ~\cite{slater_atomic_1964}. % citation
-
+  ring (2.8~\AA) and two times the carbon atom electronic radius (0.7~\AA)~\cite{slater_atomic_1964}.
+  %MRSF: specify below what 'here' is.  This graph, this study, this section?
   Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
@@
   We gave the simplified models the same amount of disorder present in the atomistic
-  simulations. We observe two sources of disorder: thermal motion of atoms
-  and quenched disorder which is created by rapid structural rearrangement during 
+  simulations. We observe two sources of disorder in our atomistic simulations: thermal motion of atoms
+  during the simulation and quenched disorder created by rapid structural rearrangement during 
   early equilibration and is largely locked into place for the remainder of the 
-  simulation. We measured thermal disorder by calculating the standard deviation of 
+  simulation, even at the 100 ns time scale. We measured thermal disorder by calculating the standard deviation of 
   the distribution of head group COM positions from their average positions.
@@
   equally spaced points surrounding the pore center. This method for calculating 
-  quenched disorder inherently includes thermal disorder.
+  quenched disorder inherently includes the convoluted thermal disorder.
 
@@
   generated with point scatterer placement based on the quenched disorder seen in
-  atomistic simulations. The quenched disorder is greater in  magnitude than thermal 
+  atomistic simulations. The quenched disorder observed in the atomistic simulations is greater in magnitude than thermal 
   disorder (See Table~\ref{table:quenched_disorder} in Section~\ref{section:rpi}).
-  This method assumes that the timescales for large scale rearrangements of the
+  %MRSF: How much greater? Be a bit more specific (10% greater?  100x times greater?)
+  This method 
+  %MRSF: specify exactly what of the preceeding is meant by ``this method''
+  assumes that the timescales for large scale rearrangements of the
   system are much longer than what we can feasibly simulate.
@@
   we created a cross-linking algorithm that one can apply to equilibrated structures. 
-  The primary purpose of cross-linking is to create a mechanically robust membrane.
+  The primary purpose of cross-linking experimentally is to create a mechanically robust membrane.
   For that reason, we are not concerned with replicating the kinetics of the reaction, 
@@
   the next group of eligible carbons atoms.
+
+  \subsection{Source code}
+  %MRSF: Suggest moving these references to where each code is described instead of separately here.
+  %BJC: the hyperref package really messes up the labels
+  The python scripts used to simulated XRD patterns are publicly available online at \\
+  \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Python scripts used to conduct
+  all other post-simulation trajectory analysis, are also available online at \\ 
+  \texttt{https://github.com/bencoscia/llcsim}.
+  %BJC: llcsim repository only contains necessary scripts. Should probably move to Shirts-group repo
 
@@
   Our simulations best support a model built with 5 monomer columns per pore based on
-  the measured equilibrated pore-to-pore distances. To discern the density of
-  monomer columns in each pore, addressing Question \ref{point:monomernum} above, we ran
+  the measured equilibrated pore-to-pore distances. To identify the density of
+  monomer columns around each pore, addressing question \ref{point:monomernum} in the introduction, we ran
   simulations of systems created with 4--8 columns per pore. We built systems in both
@@
 
+  %MRSF: is there some comment that you can make above about the disordered ones not having many of the structures seen in WAXS to make it clearer that they are not as interesting from the get-go, and provide more details in the follow up sections?
+
   %MRS7: maybe above say where (i.e.
@@
 
-  Systems built with 5 columns in each pore equilibrate to a pore spacing that
+  %MRSF: I',m experimenting with ``columns _around_ each pore'' instead of ``Columns _in_ each pore''. Around makes the geometry a bit more explicit. 
+  Systems built with 5 columns around each pore equilibrate to a pore spacing that
   is most consistent with the experimental value of 4.12 nm derived from SAXS
@@
   disordered basin systems built with 6 columns-per-pore agree with experimental
-  pore-to-pore distances within error, but stack too far apart. Those in the
+  pore-to-pore distances within error, but stack too far apart. 
+  %MRSF: not clear of the disordered ones below are for 5 or 6 columns
+Those in the
   disordered sandwiched and disordered parallel displaced configurations stack
+  %MRSF: maybe use $\sim$ instead of ca., for consistency?
   $\sim$~4.87 and 4.94 \AA~apart respectively, which is ca. 1.2~\AA~further apart
@@
   0.9 \AA~further apart than experiment (see 
-  Table~\ref{table:correlation_length}).  The remainder of this discussion will
+  Table~\ref{table:correlation_length}).  The remainder of this discussion will therefore 
   focus on the analysis of systems built with 5 columns per pore.
@@
   \subsection{Simulated XRD comparison to 2D-WAXS data}
-
+  %MRSF: be consistent on ``Section'' vs. ``section''. Check j chem phys b papers for which one is more correct. 
   We can better understand the structure of the system by simulating XRD
-  patterns produced from equilibrated MD trajectories (See
-  section~\ref{method:xrd}) and comparing them to experiment, addressing
-  Question~\ref{point:xrdmatch}. We tested systems built with 5 columns per pore
+  patterns produced from equilibrated MD trajectories (see
+  section~\ref{method:xrd}) and comparing these simulated patters to experiment, addressing
+  question~\ref{point:xrdmatch} in the introduction. We tested systems built with 5 columns per pore
   in the parallel displaced and sandwiched configurations at
@@
   with the most unambiguous XRD features, the pore-to-pore spacing
-  and the stacking distance.  We generated simulated patterns using the locally
-  equilibrated portion of each simulation trajectory (See
+  and the stacking distance, as described in section~\ref{section:mon_per_pore}.  We generated simulated patterns using the locally
+  equilibrated portion of each simulation trajectory (see
   Section~\ref{method:equil_time}). There are two important factors to take into
@@
   respect to the membrane plane. We found that it equilibrates to an average tilt
-  angle of -2\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle
+  angle of -2\degree~(Figure~\ref{fig:tilt}), 
+  %MRSF: any uncertainty analysis for the 2% that can be included?
+  far from the 37\degree~tilt angle
   previously used to explain R-spots. Even when we placed position restraints on
@@
   and we do not achieve the timescales necessary for them to rearrange into a
-  necessarily more tightly packed configuration. We equilibrated the
+  necessarily more tightly packed configuration. To test the this chain-packing hypotheses, 
+  we equilibrated the
   system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
@@
   stabilize the hexagonal phase at 500 K, we placed harmonic restraints with 
-  force constants of 1000 $kJ\ mol^{-1}\ nm^{-2}$ between head group COMs
+  force constants of 1000 kJ mol$^{-1}$ nm$^{-2}$ between head group COMs
   within each column as well as between head group COMs in
@@
 	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
-	  correlation length for (d) because there are no clear peaks. We assume that its
+	  correlation length for (d) because there are no clear peaks. We assume that this
 	  correlation length is less than the vertical distance between monomers.}\label{fig:correlation}
@@
   \end{subfigure}
+  #MRSF: yellow not legended?
   \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
-  thermal noise in the $z$-direction, however the $q_r$ cross-section profile does
+  thermal noise in the $z$-direction; however, the $q_r$ cross-section profile does
   not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
@@
   the simulated diffraction patterns smooths out. We can demostrate this by
-  creating a simplified sandwiched configuration (simplified in the same way as
-  described above), 
-  %simple systems 
-  %MRS10: simple systems is not very exact. Point scatters that represent the head groups?
-  %BJC11: It feels redundant and wordy saying the above rather than simple systems.
-  with varying amounts of statistical correlation between columns. In the low
+  creating a simplified sandwiched configuration (as described above), 
+  with varying amounts of statistical correlation between columns (see Figure~\ref{fig:column_displacement}). In the low independent motion limit
   limit, the COM of columns are situated at the same $z$-coordinate.
@@
   other. When $f = 1$, the columns move independently and the $q_r$ cross-section
-  smooths out completely (Figure~\ref{fig:column_displacement}). Any amount of
+  smooths out completely (Figure~\ref{fig:sf_qy_sr100}). Any amount of
   dependence results in some presence of independent sharp peaks, though
@@
 
+  %MRSF: I had a bit of hard time connecting the thesis of this paragraph to the details provided.
   It therefore seems likely that the discrepancy between the intensity of
@@
   3D correlation function. When we include all $z$-slices in $g(z)$ for our
-  system, rather than restricting it to those $z$-slices within 2.1 \AA of the
+  system, rather than restricting it to those $z$-slices within 2.1~\AA of the
   center of the correlation function (Section~\ref{section:correlation_length}),
@@
   of the fit implies that the FWHM may actually be different from experiment, and
+  %MRSF: what does optimization mean here? Better forcefield or longer time? Better fitting?
   that the radial ordering of the head groups may benefit from further optimization.
@@
   \subsubsection*{Quenched disorder in ensembles of configurations}
+
+%MRSF: suggest breaking up this paragraph into 2-3 paragraphs.
+Thesis is just that we studied ensembles of short simulations,but would be clearer stronger of some of the results are separated out into their own paragraph.
 
@@
   trajectories are shown in Figure~\ref{fig:ensemble_XRD}. 
+%MRSF: maybe here break?  might need a bit of rephrasing of thesis.
   Qualitatively, the cross-sections of are nearly smooth, with only
@@
   %but present the different things that in combination would explain most of the differences.
+%MRSF: maybe split here?  Not sure, but definitely some split.
   Overall, the intensity of R-$\pi$ generated from the parallel displaced 
@@
   supporting information. %BJC15: to be added
+  %MRSF: add section number here, consistency on capitalization?
   %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
@@
   \end{subfigure}
+  %MRSF: explicitly refer to the previous graph that this is ``much smoother'' than.
   \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
@@
 
+  %MRSF: is this the clearest thesis?
+Similar to each other?
+Similar to the amount of disordered viewed in the long simulations?
+Is the symmetric nature more useful?
+I think also this paragraph should be split up more to emphasize findings.
   These short independent simulations exhibit similar amounts of quenched disorder. 
@@
   are shown in Figure~\ref{fig:offset_ecdfs} to guide the eye (colored lines). The average 
-  of all COM ECDFs is represented by the red line with the 95 \% confidence
+  of all COM ECDFs is represented by the red line with the 95\% confidence
   interval represented by the red error bars. We also calculated 
@@
   generated using the systems simulated up to this point. Here we hypothesize a
-  few initial configurations which may lead to the appearance of R-double and
+  several configurational arrangements which may lead to the appearance of R-double and
   show that we cannot achieve a long-term stable system that exhibits R-double
@@
   barrier that prevents rotation of carboxylate groups attached to phenyl rings
-  since the group extends the system's $\pi$ conjugation ~\cite{carey_organic_2011} (see Figure
+  since the group extends the system's $\pi$ conjugation~\cite{carey_organic_2011} (see Figure
   S-\ref{S-fig:carboxylate_dihedral_rb} of the Supporting Information), which is significant even considering
@@
   may be the most favorable way for them to pack. This configuration is only
-  stable for a few nanoseconds but R-double quickly fades. 
+  stable for a few nanoseconds and R-double quickly fades. 
   %MRS12: seems like unnecssary speculation below, since there are a lot of cancelling affects. 
@@
   The addition of water to the system promotes the appearance of R-double, providing
-  an answer to Question~\ref{point:water}.
+  an answer to question~\ref{point:water} posed in the introduction.
 %  through the creation of shared hydrogen bonds between water molecules and carboxylate
@@
   appear without the presence of the head groups. Water molecules must therefore play a
-  role in the structuring of the head groups since R-double does not appear in
+  role in the structuring of the head groups in these simulations since R-double does not appear in
   any dry simulations.
@@
   a separation process. We aim to further understand the pore architecture, in
-  order to address Question~\ref{point:composition}, and observe the differences,
-  if any, between the different equilibrated configurations studied so far.
-
+  order to address question~\ref{point:composition} postedd in the introduction, and observe the differences,
+  if any, between the different plausible equilibrated configurations studied so far.
+
+  %MRSF: seems like a thesis w/o supporting data - maybe merge paragraphs, or provide a survey of the findings presented below.
   %BJC6: moved this paragraph up to make the section more idea-focused
@@
   of the Supporting Information for a diagram). We averaged the histograms over at least 50 ns of equilibrated trajectory.
-
+  %MRSF: why 50 ns? 
   There is a gradient in pore composition transitioning radially from the hydrophilic 
   to the hydrophobic region, rather than an abrupt division. Based on size-exclusion 
-  experiments, we define the pore radius to be 0.6 nm~\cite{zhou_supported_2005}. 
+  experiments, the pore radius was estimated to be 0.6 nm~\cite{zhou_supported_2005}. 
+  %MRSF: see before by 'we'.  You mean previous studies? Tried to tweak.
   %MRS13: be more clear.  ``We define'' would imply from THIS study, but I think you are just talking about other studies.
@@
   %MRS8: I actually think it might add understanding  I would label it as ``experimentally estimated size-exclusion radius''.
-  The system does not confine
+  However, the simulations do not confine
   sodium ions and head groups to just within this experimentally-defined pore region. For dry systems,
   19\% of sodium ions exist outside the pore region (except sandwiched, ordered basin,
-  where 16\% are outside the pore). Additionally, we see that in all cases, about 
+  where 16\% are outside the pore). Additionally, in all cases, about 
   3\% of the plotted tail density is located within the pore region (except ordered sandwiched,
@@
   We observe slow dynamics in our system. Typical diffusion constants for columnar
-  liquid crystals have been reported to be between $10^{-11}~ m^2/s$ 
-  \cite{dong_translational_1984} and $10^{-14}~m^2/s$ \cite{dvinskikh_molecular_2002}. 
+  liquid crystals have been reported to be between $10^{-11}~ \mathrm{m}^2/\mathrm{s}$ 
+  \cite{dong_translational_1984} and $10^{-14}~\mathrm{m}^2/\mathrm{s}$ \cite{dvinskikh_molecular_2002}. 
+  %MRSF: see below comment; if not LLC's we should qualify this (electrostatics would likely make slower, since larger
+  %energies involved.
   %MRS13: are these hydrophulic/hydrophopic LC?  Once with electrostatic driving forces are likely 
@@
   We measured the diffusion constants of monomers in each of the systems we
-  studied (see Table S-\ref{S-table:msd} of the Supporting Information) and learned that they are all on the order of
-  $10^{-14}~m^2/s$. However, since on this timescale, no monomers move
-  a full `level` above or below, this may be an overestimate. This slow speed is
+  studied (see Table S-\ref{S-table:msd} of the Supporting Information) and find they are all on the order of
+  $10^{-14}~\mathrm{m}^2/\mathrm{s}$. However, since on this timescale, no monomers move
+  a full `level' above or below, this may be an overestimate. This slow speed is
   not entirely surprising considering how densely the monomers are
@@
   equilibrate to a stacking distance that is too large compared to experiment. 
-  While this may be in large part due to the force field's inability to model aromatic
+  As discussed in section~\ref{section:rpi},
+  while this may be in large part due to the force field's inability to model aromatic
   interactions, it is also possible that the monomer tails do have enough time to pack 
@@
 
-  The calculated value of ionic conductivity is 5 times higher than experiment because 
+  The calculated value of ionic conductivity is 5 times higher than experiment likely because 
   we simulated infinitely long, aligned pores. The ionic conductivity measurement 
@@
 
-  \subsection{Effect of Cross-linking}\label{section:xlink}
+  \subsection{Effect of cross-linking}\label{section:xlink}
 
@@
   observation has possible implications for the reproducibility of the experimental
-  results from Feng et al. since they claim that their membrane is completely dry.
+  results from Feng et al. since they specify that their membrane is synthesized dry.
 
@@
   ionic conductivity drops by a factor
-  of ca. 1.5, in closer agreement with experiment, the pore spacing decreases and
+  of $\sim$1.5, in closer agreement with experiment, the pore spacing decreases and
   the membrane becomes thicker; however, all changes are relatively minor, 
@@
 
+%MRSF: get rid of google books id on ref 45.
   \clearpage

### 2018-10-07 Ben_Manuscripts/structure_paper/supporting_information.tex
Comments on supporting information.

@@
 
-	\item \textit{Create monomer structure file with connectivity} : We
+	\item \textit{Create monomer structure file with connectivity}: We
 	drew atomistic structures using MarvinSketch
@@
 
-	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using
+	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}}: Using
 	the .pdb structure file as input, we ran
@@
 	output of \texttt{antechamber} to create Amber topology files. A detailed
-	tutorial can be accessed elsewhere \cite{walker_antechamber_nodate}.
-
-	\item \textit{Create GROMACS topologies from Amber output} : The output
+	tutorial for using \texttt{LEaP} for parameterizationcan be accessed elsewhere \cite{walker_antechamber_nodate}.
+
+	\item \textit{Create GROMACS topologies from Amber output}: The output
 	of \texttt{LEaP} is a .inpcrd and a .prmtop file which are Amber topology
@@
 
-	\item \textit{Perform a simulated annealing procedure on the monomer} :
+	\item \textit{Perform a simulated annealing procedure on the monomer}:
 	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
@@
 	system from 1000 K to 50 K over the course of 10 ns. We randomly chose a monomer
-	configuration from the last 10 \% of the trajectory.
+	configuration from the last 10\% of the trajectory.
 
@@
 
-	\item \textit{Anneal again to get final structure} : We repeated the
+	\item \textit{Anneal again to get final structure}: We repeated the
 	same simulated annealing procedure using the monomer topology with
 	\texttt{molcharge} charges. A random monomer configuration was pulled from the
-	last 10 \% of the trajectory and was used to build all assemblies reported
+	last 10\% of the trajectory and was used to build all assemblies reported
 	(Figure~\ref{fig:monomer}).
@@
   Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
-  box with a volume of 660 $nm^3$, 25\% larger than those used to create ordered unit
+  box with a volume of 660 nm$^3$, 25\% larger than those used to create ordered unit
   cells we studied. We tested systems with semi-isotropic and anisotropic pressure 
@@
 
-  We chose to build all systems using 20 monomers per column. We made this choice
+  We chose to build all systems using 20 monomers per column, i.e.
+for a simulation with 5 columns around each pore, there are 100 monomers per pore, and 400 monomers per simulation.
+We made this choice
   by considering a number of factors that directly affect the quality of our results. 
-  Clearly, choosing a small number of layers will cause the system to suffer from 
-  finite size effects. Even in our 20 monomer-per-column system, axial correlations
+  Clearly, choosing a smaller number of layers will cause the system to suffer from 
+  larger finite size effects. Even in our 20 monomer-per-column system, axial correlations
   between stacked monomers persist throughout the entire correlation function (see
@@
   correlation function will eventually fully decay but it is not worth the 
-  computational expense. Regardless, the correlation lengths calculated from 20
+  computational expense. We do find that the correlation lengths calculated from 20
   monomer per column simulations are in sufficient agreement with experiment. 
-
+  %MRSF: if 10 monomers per column gave inconsistent pores when tried, might as well mention that here. 
   \begin{figure}[!htb]
@@
 
-		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
+		\item 45 \AA~: A pore spacing of 45 \AA~is about 10\% larger
 	than the experimental value. This systems exhibits the smallest response to our 
@@
 
-	\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \%
+	\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20\%
 	larger than the experimental value. Once the restraining potential reaches 56
@@
 	spacings.
-
+        %MRSF: I think this is the spread in a single pore, not the average pore.
+Should probably make it clearer to readers which it is (i.e.
+uncertainty in one, not uncertainty in mean of the four).
   \end{enumerate}
@@
 		the location of all other pore centers.}
-	\label{fig:p2p_diagram}
+	\label{fig:p2p_diagram}  %MRSF: this label is multiply defined. 
   \end{figure}
@@
   box vectors, however this technique does not fully capture the uncertainty
-  in the pore-to-pore distances.
+  in the individual pore-to-pore distances.
 
@@
   System                         & Pore Spacing ($nm$) & Pore Spacing ($nm$)              \\
-                                 & Pore centers        & $\dfrac{x\ box\ vector}{2}$ ($nm$) \\ 
+                                 & Pore centers        & $\frac{1}{2}(x\ box\ vector)$ ($nm$) \\ 
   \midrule
@@
   relationship. We also measured ionic conductivity using a second method, 
+  %MRSF: Don't capitalize Collective Diffusion. Also, add citation on first mention.
   termed the Collective Diffusion model, for robustness. The collective 
@@
   \centering
+  % seems to be missing in the repository? tilt_cat.png
   \includegraphics[width=0.5\textwidth]{tilt_cat.png}
@@
 
+  %MRSF: isn't this picture the same in the main draft of the document. Probably wouldn't have occured.
   \begin{figure}[!htb]
@@
 
+  %MRSF: probably needs some context, since this is for a force field, not for QM.
+Did you have plots for several different force fields, which all are presumably trying to capture the QM that all basically gave the same results?
+That would be better evidence.
   \begin{figure}[!htb]

### 2018-10-08 Ben_Manuscripts/structure_paper/supporting_information.tex
Edits

@@
   monomer per column simulations are in sufficient agreement with experiment.
-  %MRSF: if 10 monomers per column gave inconsistent pores when tried, might as well mention that here. 
+
   \begin{figure}[!htb]
@@
 	pore spacing for each pore over all bootstrap trials. Using the 5 average 
-	pore-to-pore distances, we calculate the spread with:
+	pore-to-pore distances, we calculate the spread in a single pore-to-pore distance 
+	with:
 	\begin{equation}
@@
 	spacings.
-        %MRSF: I think this is the spread in a single pore, not the average pore.
-Should probably make it clearer to readers which it is (i.e.
-uncertainty in one, not uncertainty in mean of the four).
   \end{enumerate}
-  \begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
-	\caption{There are five pore-to-pore distances that are equal in a perfect
-		hexagon. If each number in the diagram represents the center of a
-		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
-		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
-		are independent. For example, the distance from 1 to 4 is defined by
-		the location of all other pore centers.}
-	\label{fig:p2p_diagram}  %MRSF: this label is multiply defined. 
-  \end{figure}
+
+%BJC: included in a figure above
+%  \begin{figure}[!htb]
+%	\centering
+%	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
+%	\caption{There are five pore-to-pore distances that are equal in a perfect
+%		hexagon. If each number in the diagram represents the center of a
+%		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
+%		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
+%		are independent. For example, the distance from 1 to 4 is defined by
+%		the location of all other pore centers.}
+%	\label{fig:p2p_diagram}  
+%  \end{figure}
 
@@
   relationship. We also measured ionic conductivity using a second method, 
-  %MRSF: Don't capitalize Collective Diffusion. Also, add citation on first mention.
-  termed the Collective Diffusion model, for robustness. The collective 
+  termed the collective diffusion model\cite{liu_collective_2013}, for robustness. The collective 
   diffusion model measures the movement of the collective variable, Q, which
@@
 
-  \section{Ensemble of ordered sandwiched configurations}
+  \section{Ensemble of ordered sandwiched configurations}\label{section:sandwiched_ensemble}
 
@@
   %MRSF: isn't this picture the same in the main draft of the document. Probably wouldn't have occured.
+  %BJC: it's not identical. The main text uses the parallel displaced data.
   \begin{figure}[!htb]
@@
 
-  %MRSF: probably needs some context, since this is for a force field, not for QM.
-Did you have plots for several different force fields, which all are presumably trying to capture the QM that all basically gave the same results?
-That would be better evidence.
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=0.5\textwidth]{carboxylate_dihedral_rb.png}
+  It is most energetically favorable for the carboxylate group attached to the monomer
+  head groups to stay coplanar with the phenyl group to which it is attached
+  (Figure~\ref{fig:carboxylate_dihedral_rb}). Although GAFF may over-predict the penalty
+  for deviating from its minimum energy configuration relative to those calculated 
+  by Rakitin and Pack~\cite{rakitin_necessity_2005} and Nelson and
+  Borkman~\cite{nelson_internal_1998}, they all show that there is an appreciable barrier
+  to rotation about the carboxylate-phenyl bond. The potential energy reaches its maximum
+  at rotation angles corresponding to a carboxylate group that is antiparallel to the 
+  plane of the phenyl ring to which it is attached (90\degree and 270\degree).
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.5\textwidth]{carboxylate_dihedrals.pdf}
   \caption{A potential energy diagram for the dihedral angle about the carbon-carbon bond of
-  a carboxylate group attached to an aromatic ring, using parameters from the generalized amber 
-  forcefield. It is energetically favorable for the carboxylate group to stay in plane with 
-  the aromatic ring. There is a large energy penalty as the dihedral becomes antiparallel to 
-  the plane of the aromatic ring.}\label{fig:carboxylate_dihedral_rb}
-  \end{figure}
-
+  a carboxylate group attached to an aromatic ring, using parameters from GAFF (blue), 
+  Rakitin (orange) and Borkman (green). It is energetically favorable for the 
+  carboxylate group to stay in plane with the aromatic ring. There is a large energy 
+  penalty as the dihedral becomes antiparallel to the plane of the aromatic 
+  ring.}\label{fig:carboxylate_dihedral_rb}
+  \end{figure}
+
+  \clearpage
 % BJC: not necessary
@@
 
+  \clearpage
   \section{The role of water in the appearance of R-double}\label{section:rdouble}

### 2018-10-08 Ben_Manuscripts/structure_paper/Final_Draft.tex
added missing files

--- 2018-10-07 Ben_Manuscripts/structure_paper/Draft.tex
@@
 \affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
-%\author{Richard D. Noble}
 \author{Douglas L. Gin}
@@
 \begin{document}
-%MRS13: we might end up adjusting the author list a bit; I will ask Matt where he thinks he and Joe should go.
-I will talk to Rich when we get this going; not clear that he actually has contributed.
-But that's my job.
+
   \graphicspath{{./figures/}}
@@
   \begin{abstract}
+
+  %NOTE: all deleted comments are still in Draft.tex
 
@@
 
-  %MRSF: I changed the description of the ``demonstrating'', ``showing'' verbs to present tense.
-The experiments are past tense, but the ``showing'' is present tense, since it is occuring while the reader is reading (like in a presentation - you are showing as they listen).
   \end{abstract}
@@
 
-  % BJC5: Note to self -- how to use latex xr : Figure S~\ref{S-fig:monomer_color_coded}
-
   More highly selective nanoporous membranes would be extremely useful 
-  %in order to perform 
   in performing complex aqueous separations with seawater and various 
-  %sources 
-  types of
-  wastewater. 
-  For exaple, 
-  Sodium chloride and boron in seawater
+  types of wastewater. For example, Sodium chloride and boron in seawater
   \cite{fritzmann_state---art_2007} and organic micropollutants found in
-  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} represent just a few of the diverse contaminants 
-  of water sources. By efficiently
+  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} represent
+  just a few of the diverse contaminants of water sources. By efficiently
   separating contaminants from feed solutions with highly selective membranes,
@@
 
-%MRSF: a few selelected edits above, but I think strikes the right balance.
-% More highly selective membranes would be extremely useful for both the
-% recovery of valuable dissolved species from and the purification of complex
-%  aqueous solutions. The supply of fresh water is being increasingly strained
-%  by population growth, industrialization and climate change
-%  \cite{elimelech_future_2011}. Consequently, people are turning towards
-%  treatment of unconventional water sources such as seawater and wastewater. 
-%  In addition to obtaining fresh water from them, these water sources, 
-%  particularly municipal and industrial wastewater, have been found to contain 
-%  valuable resources which can be separated using highly selective membranes~\cite{sales_resource_2015}.
-  % make possible with selectively permeable membranes -- better than thermal distillation
-
- % BJC14: (2) existing nanoporous membranes + drawbacks
-
   Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
@@
   in size and smaller, including 
-  %as well as 
   %MRSF: this does seem to blend RO and NF together; is this correct, or are there important differences that should be outlined?
-  ions. However, the porous architecture of
-  commercially available RO and NF membranes lack uniformity, which severely impacts their
+  %BJCF: tried to differentiate them
+  ions. However, commercially available amorphous RO membranes and porous NF
+  membranes lack uniformity, which severely impacts their
   selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
@@
   selectivity.
-
-  % BJC14: (3) justification for why nanostructured membranes are a good idea for this
-  % long-term route towards highly selective membranes are those that are nanostructured
 
@@
   need for new materials that could provide scalable nanostructured porous membranes.
-
-%BJC14: zeolites aren't really nanostructured
-% Zeolites have sub-nm
-%  pores with a narrow pore size distribution, and MD simulations of these
-%  materials show that they exhibit complete rejection of solvated ions
-%  \cite{murad_molecular_1998}- however, experimental rejection was low and
-%  attributed to interstitial defects formed during membrane synthesis
-%  \cite{li_desalination_2004}.
-
-%  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
-%  filtration processes that can be used to separate solutes on the order of 1 nm
-%  in size and smaller, as well as ions. Both apply hydraulic pressure to the feed
-%  solution in order to overcome osmotic pressure and force water and unfiltered
-%  components through the membrane. RO membranes typically have a thin film
-%  composite architecture which, at minimum, consists of a porous support layer
-%  and a dense polymer active layer. Separation occurs based on the differences in
-%  solubility and diffusivity of feed solution constituents in the active layer.
-%  Nanofiltration membranes have explicit pores on the order of 1 nm in diameter
-%  which are typically tortuous and polydisperse in size. They separate primarily
-%  based on size exclusion as well as Donnan exclusion if the membrane has a
-%  surface charge~\cite{van_der_bruggen_review_2003}.
-
-  %MRS14: is selectivity towards water important, or selectivity against what one wants filtered out?
-%  The energy consumed during the purification of seawater and wastewater 
-%  using RO and NF membranes can be reduced by increasing their selectivity 
-%  towards water \cite{werber_materials_2016}. While researchers often focus on
-%  improving membrane permeability, the flux of water through a given membrane,
-%  it has been shown that increased water permeability only slightly decreases
-%  energy requirements \cite{cohen-tanugi_quantifying_2014}.
-%  since the main energy requirement for a membrane separation is that needed
-%  to create the hydraulic pressure necessary in order to overcome the 
-%  osmotic pressure of the feed solution\cite{cohen-tanugi_quantifying_2014}. 
-%  Often times, multiple membrane passes are required in order to sufficiently
-  %MRS14: not sure the boric acid part is that relevant, since we don't really talk about 
-  %that in the rest of the paper.
-%  reduce contaminant levels. For example, boric acid is toxic to humans and 
-%  is present in seawater at levels well above acceptable drinking standards.
-%  It is difficult to sufficiently separate boric acid in a single pass, meaning
-%  multiple passes are needed and energy requirements nearly double \cite{fritzmann_state---art_2007}.
-%  This is necessary in the case where high-purity water
-%  is needed \cite{singh_production_2009}, when separating small neutral solutes \cite{ozaki_rejection_2002} or
-%  when removing boric acid from seawater \cite{fritzmann_state---art_2007}.  
-%  The most effective way to reduce energy consumption
-%  would be to reduce the number of membrane passes for a given system using 
-%  more selective membranes. 
-%   More highly selective membranes have the potential
-%  to reduce the number of membrane passes in addition to eliminating the need 
-%  for other post-treatment steps necessitated by incomplete separations.
-  %dissolved species which negatively
-%  affect human health.
-
-%  Not only will increased selectivity reduce the energy consumption of membrane
-%  processes, but it offers a way to recover valuable resources from the feed 
-%  streams. Municipal and industrial wastewaters are contaminated by harmful
-%  micropollutants, but also contain valuable dissolved solutes. Micropollutants include
-%  pharmaceutical and personal care products, hormones, pesticides and industrial
-%  chemicals, all of which have adverse effects on human health even at low 
-%  concentrations\cite{schwarzenbach_challenge_2006}. A selective membrane has the % There is a need for membranes
-%  potential to reject these components while still allowing the passage of valuable 
-%  resources for further processing and recovery.
-
-%  Municipal wastewaters are rich in carbon, nitrogen and phosphorus-containing 
-%  compounds. The recovery of such products, which can be achieved using a 
-%  selective membrane, has numerous potential uses \cite{sales_resource_2015}. 
-%  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
-%  production which will help meet global food demand as population continues
-%  to increase \cite{xie_membrane-based_2016}.
-
-  %MRS14: could possibly be food details, if selective membranes are the key to purifying industrial waste waters. 
-%  Industrial waste-waters are often quite complex with up to six times more 
-%  total dissolved solids than seawater\cite{werber_materials_2016}. For example, flowback water, produced
-%  during hydraulic fracturing of shale formations consists of relatively high
-%  concentrations of salts, metals, and soluble organic compounds. The majority
-%  of this water is disposed through deep well injection, however there is a growing public concern about
-%  its management which has prompted the use of separation technologies such as 
-%  RO and NF in order to reduce the volume of contaminated water~\cite{gregory_water_2011}.
-%  Some of the dissolved organic compounds in flowback water, such as acetate, 
-%  are potentially valuable and can be recovered with highly selective membranes
-%  ~\cite{dischinger_application_2017}.
-
-%  More highly selective membranes would be extremely useful for the recovery of
-%  dissolved species in complex aqueous and organic solutions. For example,
-%  selective membranes can further progress forward osmosis processes by reducing
-%  the cost of separating potable water from draw
-%  solutions~\cite{mccutcheon_novel_2005}. Additionally, flowback water (FW)
-%  produced during hydraulic fracturing is a complex wastewater full of
-%  potentially valuable dissolved organic compounds such as acetate that can be
-%  recovered using highly selective membranes \cite{dischinger_application_2017}.
-%  Finally, a significant amount of nitrogen and phosphorus from fertilizer is
-%  found in wastewater. Selective membranes offer a route towards low energy
-%  nutrient recovery from these wastewaters which can help sustain fertilizer
-%  production and subsequently food production into the future
-%  \cite{xie_membrane-based_2016}.
-  % as we near peak production of minable phosphorus rock .
-
-%  There is increasing pressure to reuse
-%  hydraulic fracturing water rather than dispose of it in order to reduce social
-%  and environmental impacts as well as cost \cite{theodori_hydraulic_2014}.
-%  Rather fully than dispose of the wastestream generated in the recycling
-%  process, we can instead use highly selective membranes in order to successfully
-%  recover useful compounds.
-
-%  The permeability-selectivity tradeoff is a well-known problem in the membrane
-%  separations community. It is difficult to increase the permeability of a 
-%  desired molecular or atomic species, while maintaining the same retention of
-%  an undesired species.
-
-%  Current commercial RO and NF membranes suffer limitations to their selectivity
-%  because their structures incorporate some degree of randomness. Although scalable, their 
-%  fabrication involves the spontaneous assembly of polymers into disordered structures
-%  which offer separation pathways that are tortuous and polydisperse in size 
-%  \cite{werber_materials_2016}. Tortuosity increases the effective length that a 
-%  solute must travel, while polydispersity limits membrane selectivity.
-
-%  This makes overcoming the well-known 
-%  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
-%  the permeability of a desired molecular or atomic species, while maintaining the 
-%  same retention of an undesired species \cite{werber_materials_2016}.
-
-%MRS5: under solution-diffusion, then the free energy to partition into the membrane is important as well, correct?
-%  Selective separation by a semipermeable membrane barrier can be broken into two
-%  steps: barrier entry and transport through the barrier. A solute's ability to
-  % BJC: can also come up with a third step: exit. Which I think is mostly chemical potential gradient
-%  enter a given membrane barrier is decided by its size, shape, charge, polarity
-%  and how those factors combine to interact with the membrane material. The same
-%  properties affect the rate at which a solute travels across the barrier. Since
-%  undesired solutes may still enter the membrane, their diffusion rates relative
-%  to desired solutes are important
-%  \cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}. To achieve optimum
-%  selectivity, it is necessary to design membranes in a way that one can tune the
-%  relative diffusivities of desired and undesired solutes.
-
-%BJC14: probably unnecessary?
-%  Selective separation by a semipermeable membrane barrier is a function of the
-%  geometric and chemical interactions of solutes with the membrane material. A
-%  molecule's size, shape, charge and polarity combine to determine the degree to
-%  which a solute partitions into a membrane and how fast it travels through the
-%  membrane. To separate a component from a mixture, one must understand how to
-%  design membranes in order to tune the relative transport rates of desired and
-%  undesired solutes\cite{gin_polymerized_2008,wijmans_solution-diffusion_1995}.
-
-% BJC: Maybe I don't even need to dive into explaining RO and NF.
-%  Reverse osmosis (RO) and nanofiltration (NF) are membrane-based separation
-%  processes widely used to create potable or reusable water by removing salts and
-%  other dissolved compounds from water sources. RO membranes are typically thin
-%  film composite (TFC) membranes with a porous support layer and a dense
-%  crosslinked polymer active layer which  separates all solutes from water. NF
-%  membranes have porous architectures with pores on the order of 1 nm in size
-%  which separate primarily based on solute size
-%  \cite{van_der_bruggen_review_2003}.
-
-  % BJC14: (4) justify LLCs
 
@@
   form the same hexagonal columnar structure which, in the literature, has been
-  referred to as the Col\textsubscript{h} thermotropic
-  phase\cite{feng_scalable_2014}. 
-  % BJC6: maybe not a necessary detail
-%  The most
-%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
-%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
+  referred to as the Col\textsubscript{h} thermotropic phase\cite{feng_scalable_2014}.
   Q\textsubscript{I}-phase membranes consist of a tortuous network of three
@@
   hexagonally packed LC domains of the H\textsubscript{II}-phase
-  generally form mutually unaligned domains, which 
-  %are detrimental to 
-  hurts
-  membrane permeability. This domain scale misalignment
-  had inhibited further development of this technology, and research efforts
-  were focused on the Q\textsubscript{I} phase, whose geometry does not require
-  alignment~\cite{zhou_new_2007}.
-
-%MRS5: maybe less about Q_I since it's not in this paper?  The introduction should be an introduction to the paper.
-%  The most promising Q\textsubscript{I} phase for membrane
-%  applications forms at 70\degree C when monomer is mixed with c.a.~20 wt\%
-%  glycerol\cite{carter_glycerol-based_2012}. The Q\textsubscript{I} phase
-%  consists of a network of three dimensionally interconnected pores (See
-%  Figure~\ref{fig:bcc_phases}). This complex geometry effectively adds a degree
-%  of tortuosity to the membrane which prevents optimal through-plane transport.
-%  Despite the geometric differences between the Q\textsubscript{I} and
-%  H\textsubscript{II} phase, the chemical environment within the pores is
-%  expected to be similar, and either membrane should be highly selective.
-
-%  % BJC: I like this figure, but I don't know if it is necessary in the main body. i  % Maybe move to supplemental. Thoughts?
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%        \centering
-%        \includegraphics[trim=-2cm 0 0 0, clip, height=4.5cm]{Dibrpyr14.eps}
-%        \includegraphics[height=4.5cm]{bcc_phases.png}
-%        \caption{}\label{fig:bcc_phases}
-%  \end{subfigure}
-%  \hspace{1cm}
-%  \begin{subfigure}{0.45\textwidth}
-%        \centering
-%        \includegraphics[trim=0 -0.5cm 0 -0.5cm, clip, height=4.5cm]{NaGA3C11.eps}
-%        \includegraphics[height=4.5cm]{hexagonal_packing.png}
-%        \caption{}\label{fig:hII_phase}
-%  \end{subfigure}
-%%MRS5: not sure Q should be in here.  Could cut length by removing some of the detail about Q phase, since it 
-%%isn't discussed in the paper. 
-%  \caption{The choice of LLC monomer and solvent leads to different accessible liquid
-%        crystalline phases. The monomer shown in (a) forms the Q\textsubscript{I} phase
-%        in either the Ia3d (left) or Pn3m (right) space group. The surfaces shown
-%        represent the interface between the hydrophilic and hydrophobic regions of the unit
-%        cell. 
-%        %MRS7: not needed
-%        %As pictured, we assume that each region occupies an equal volume. 
-%        The
-%        monomer shown in (b) will form the hexagonal columnar phase
-%        (H\textsubscript{II} in the presence of water or Col\textsubscript{h} when no
-%         water is present) The blue region represent the hydrophilic pores while the cyan region represents the surrounding hydrophobic monomer tails.}\label{fig:bcc_v_hII}
-%  \end{figure}
-
-  %Nanostructured porous membrane materials have become increasingly popular for
-  %aqueous separations applications such as desalination and biorefinement because
-  %they offer the ability to control pore architecture at the molecular scale,
-  %thereby permitting the design of solute-specific separation membranes
-  %\cite{humplik_nanostructured_2011}. One can achieve most membrane-based aqueous separations of
-  %small molecules using reverse osmosis (RO) or nanofiltration
-  %(NF) \cite{van_der_bruggen_review_2003}. While RO and NF have seen many
-  %advances in the past few decades, they are far from perfect separation
-
-   %MRS4: these two paragraphs are perhaps not ideal.  They describe the process
-  %of making the membranes, but that is not what we need as the introduction to
-  %THIS paper.  Instead, you need to focus on the strength/issues with RO and
-  %NF that motivate this research.
-  % BJC2: The point I am trying to make is that the way the membranes are made 
-  % results in either low selectivity or low permeability. I could just state
-  % that, or give a little background on the processes to make the point more
-  % tangible
-
-  %Commercial RO membranes are typically dense thin-film composite (TFC)
-  %membranes with a porous support layer and an active layer made of a polymer
-  %matrix formed through interfacial polymerization \cite{jeong_interfacial_2007}.
-  %During interfacial polymerization, a step-growth polymerization reaction occurs
-  %at the interface of an aqueous monomer solution that has been soaked into the
-  %support layer, and an organic solution of a second monomer. The polymer matrix
-  %is dense and highly cross-linked which gives high rejections but low
-  %permeability.
-
-  %During membrane fabrication,
-  %aqueous diamine solution is allowed to penetrate into the polysulfone support
-  %layer which is then immersed in trimesoyl chloride, a compound that is
-  %immiscible in water. Diamine polymerizes with trimesoyl chloride at the
-  %solution interface and creates a thin film that physically adheres to the
-  %polysulfone support.
-
-%  solution.  Through the use of a non-solvent, a polymer-rich and polymer-poor
-%  phase is formed. A membrane is created as the polymer-poor phase forms pores in
-%  the polymer-rich phase. 
-%  During phase inversion, a thin polymer film is precipitated out of a polymer
-
-%  NF membranes are typically porous membranes made by a phase-inversion
-%  process. The most widely used phase-inversion process is immersion
-%  precipitation, during which one submerges a polymer, dissolved in a solvent, in
-%  a non-solvent. A solid, porous polymer membrane is all that remains once all
-%  solvent has been removed by non-solvent exchange
-%  \cite{smolders_microstructures_1992}.  The resultant pores are polydisperse in
-%  size, which hurts membrane selectivity. A second technique used to create NF
-%  membranes is call track-etching in which a polymer film is bombarded with
-%  charged particles, then chemically etched to create pores
-%  \cite{apel_track_2001}. The pores are uniform, which benefits selectivity;
-%  however, the membranes have a low porosity and subsequently low permeability.
-
-%MRS3: this is a little disconnected to the contents as well.  You want
-%the paper to explain the why of doing this research.  Paragraph gives background, but doesn't motivate.
-
-%  Current commercial RO membranes are thin film composite membranes with a
-%  porous support layer and an active layer made of a dense polymer matrix. The
-%  membranes are unstructured with tortuous and polydisperse diffusion pathways.
-%  Separation occurs based on differences in solubility and diffusivity of solutes
-%  within the polymer matrix \cite{wijmans_solution-diffusion_1995}. With
-%  optimization, one can exploit these differences to create a functional
-%  selective barrier. RO operation costs are suboptimal because high feed
-%  pressures are required in order to achieve a useful solvent flux.
-
-  %BJC : I don't know that this paragraph fits.  
-  %MRS3: not really.
-Maybe take a look at Osuji's recent review (2016, I think) that addresses applications of nanostructured membranes and uses.
-Could rewrite the introduction to be more about the general possibilities of nanostructured membranes, not just desalination.
-It should be an introduction to what you will talk about in the paper, not to everything related.
- % Improved RO membranes can make desalination more sustainable. Only 0.5\% of
- % the world's water is fresh. Desalination is an important source of potable
- % water, necessary in order to keep up with demand generated by a rapidly growing
- % global population. Although RO is currently the cheapest form of desalination,
- % the cost must be further decreased in order to meet demand. A typical seawater
- % desalination process requires feed pressures in the range of 800 to 1000 psi
- % \cite{fritzmann_state---art_2007}. By designing better membranes for
- % desalination, we can achieve higher water fluxes and reduce feed pressure
- % requirements which will decrease the cost of fresh water production.
- % \cite{humplik_nanostructured_2011}.
-
-  % financially straining developing regions and contributing strongly to
-  % CO\textsubscript{2} emissions. \cite{mcginnis_global_2008} Moreover,
-  % designing RO membranes to achieve targeted separations of specific solutes
-  % in a complex feed solution is nearly impossible
-
-  %NF was introduced as an intermediate between RO and ultrafiltration, having
-  %the ability to separate organic matter and salts on the order of one nanometer
-  %in size. Explicit pore pathways running through the thickness of the membrane
-  %permit high solvent fluxes at lower pressures than RO. NF membranes typically
-  %have a surface charge resulting from ionizable groups which affords separation
-  %of ions smaller than the pore radius by the mechanism of Donnan exclusion
-  %\cite{van_der_bruggen_review_2003}. NF is often used as a precursor to reverse
-  %osmosis since it can efficiently remove a significant portion of dissolved
-  %solutes. Following NF pretreatment, RO can further purify the permeate. 
-  %Unfortunately, NF membranes, like RO, possess a pore size
-  %distribution which limits their ability to perform precise separations
-  %\cite{bowen_modelling_2002}.
-
-%  The permeability-selectivity tradeoff has the potential to be overcome by
-%  designing membranes at the molecular level. Next-generation nanoporous
-%  membranes with high selectivity, permitted by a precisely controlled pore size,
-%  and high permeability, allowed by its porous architecture, have the potential to
-%  replace traditional RO and NF membrane technologies.
-
-%MRS3: I think that this paragraph probably should be couched in terms of what they COULD do, since are not widely used yet.
-%MRS3: if talking about existing membranes, should cite performance.
-%  Nanostructured membranes can bypass many of the performance issues which
-%  plague traditional NF and RO membranes. One can accomplish targeted separations
-%  with high selectivity by tuning shape, size and functionality of the molecular
-%  building blocks which form these materials. As a result, solute rejecting pores
-%  can have their sizes tuned uniformly, resulting in strict size cut-offs.
-%  Entirely different mechanisms may govern transport in a given nanostructured
-%  material which can inspire novel separation techniques.
-
-%  Development of nanostructured porous materials has been limited by the
-%  ability to synthesize and scale various fundamentally sound technologies.
-%  Graphene sheets are atomically thick which results in excellent water
-%  permeability but defects during manufacturing severely impact selectivity
-%  \cite{cohen-tanugi_multilayer_2016}. Molecular dynamics (MD) simulations of
-%  carbon nanotubes show promise \cite{humplik_nanostructured_2011}, but synthetic
-%  techniques are unable to achieve scalable alignment and pore monodispersity
-%  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Zeolites have sub-nm
-%  pores with a narrow pore size distribution, and MD simulations of these
-%  materials show that they exhibit complete rejection of solvated ions
-%  \cite{murad_molecular_1998}- however, experimental rejection was low and
-%  attributed to interstitial defects formed during membrane synthesis
-%  \cite{li_desalination_2004}. Consequently, there is a need for a scalable
-%  nanostructured porous membrane.
-
-%  Polymeric membranes based on self-assembling lyotropic liquid crystals (LLCs)
-%  are suitable candidates for aqueous separation applications. LLCs are
-%  amphiphilic molecules that share the characteristic ability of nanostructured
-%  porous membrane materials to create highly ordered nanostructures with the
-%  added benefits of low cost and synthetic techniques feasible for large-scale
-%  production \cite{feng_scalable_2014}. LLC systems created by the monomer
-%  Na-GA3C11 (Fig.~\ref{fig:monomer}) have been extensively studied experimentally
-%  \cite{feng_scalable_2014,smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_thin_2016}.
-%  The neat Na-GA3C11 monomer forms the thermotropic liquid crystalline (TLC)
-%  Col\textsubscript{h} phase (Fig.\ref{fig:assembly}). The presence of ca. 10
-%  wt\% added water results in formation of the lyotropic H\textsubscript{II}
-%  phase. In both cases, Na-GA3C11 monomers assembles into mesophases made of
-%  hexagonally packed, uniform size, cylinders with hydrophilic head groups
-%  oriented inward towards the cylinder center. This LLC assembly is then
-%  polymerized in situ to form a cross-linked polymer network to stabilize the
-%  structure. The hydrophilic region can act as a pore for aqueous separations
-%  \cite{zhou_supported_2005}.  One can envision tailoring the pore region for
-%  specific separations by changing the monomer chemistry
-%  \cite{resel_h2-phase_2000}.
-
-%  Research into the H\textsubscript{II} phase of polymerized LLC membranes has
-%  been revived in recent years. 
-%  During early stages of exploration, hexagonal
-%  mesophases formed by Na-GA3C11 (Figure~\ref{fig:assembly}) could not be
-%  macroscopically aligned, resulting in low flux membranes, and no clear route
-%  towards scalable and economical filtration. 
-%  For this reason, research efforts
+  generally form mutually unaligned domains, which hurts membrane permeability.
+  This domain scale misalignment had inhibited further development of this technology,
+  and research efforts were focused on the Q\textsubscript{I} phase, whose geometry
+  does not require alignment~\cite{zhou_new_2007}.
 
@@
 
-  % BJC: Not sure this figure needs to be in the paper. 
-  %MRS2: good question.  It helps give people context, which is necessary to
-  %move forward.  Perhaps leave it in for now, though may need to get
-  %permission to reprint it.
-  %\begin{figure} \centering
-  %\includegraphics[width=\linewidth]{soft_confinement.png} \caption{The wedge
-  %	  shaped liquid crystal monomer (a) self assembles into mesophases with
-%		  hexagonally packed pores (b). The pores are made of stacked monomer disks. A
-%		  sub-micron-thick film is created by casting a dilute solution of Na-GA3C11/THF
-%		  solution onto a silicon substrate and and allowing the solvent to evaporate.
-%		  The thin film contains nanoporous columns which lie parallel to the film plane.
-%		  (d) When a soft PDMS pad is imposed to the thin film, with subsequent thermal
-%		  annealing, the columns align perpendicular to the film plane. (e)
-%		  Photo-cross-linking of the aligned film creates a mechanically stable thin film
-%		  with vertically aligned nanopores}~\label{fig:soft} \end{figure}
-
   \begin{figure}
@@
 		\centering
-		\includegraphics[width=\textwidth]{wedge_thick.pdf}
+		\includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
 		\caption{}~\label{fig:wedge}
@@
 		\centering
-		\includegraphics[width=\textwidth]{columns.pdf}
+		\includegraphics[width=0.6\textwidth]{columns.pdf}
 		\caption{}~\label{fig:wedge_layer}
@@
 		\centering
-		\includegraphics[width=\textwidth]{hexagonal_packing.pdf}
+		\includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
 		\caption{}~\label{fig:hex_packing_simple}
 	\end{subfigure}
-        %MRSF: in the actual paper, there would only be room for about a half-page figure, max.  Can hyou reduce the especially the c/d/e sizes so that it fully fits in a half-page figure? 
 	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
@@
   \end{figure}
-
-  % BJC14: (5) justify need for simulations
 
@@
   Donnan potential.
-  %which affects the degree to which the membrane can exclude
-  %charged species at the membrane surface.
 
@@
 
-  %BJC16: This figure could probably be cut or moved to supporting info
   \begin{figure}[!htb]
@@
 		\centering
-		\includegraphics[width=\textwidth]{cartoon_pore.pdf}
+		\includegraphics[width=0.6\textwidth]{cartoon_pore.pdf}
 		\caption{}~\label{fig:undetailed_pore}
@@
 		\centering
-		\includegraphics[width=\textwidth]{detailed_pore.pdf}
+		\includegraphics[width=0.6\textwidth]{detailed_pore.pdf}
 		\caption{}~\label{fig:detailed_pore}
 	\end{subfigure} 
-    %MRSF: will probably need smaller figures for the paper. 
     \caption{(a) Previous understanding of the pores are essentially speculations 
@@
 
-  %MRS8: I started tweaking the below, but it might be better just to eliminate.
-  % Modeling of Col\textsubscript{h} will help in modeling 
-  %H\textsubscript{II} in the future.
-  %The two phases appear to share similar structural characteristics since the
-  %pore spacings in each system are in close agreement
-  %\cite{feng_thin_2016,resel_structural_2000}.
-
-%  We used experimental small-angle X-ray scattering (SAXS) data from
-%  \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
-%  (WAXS) data (Fig.~\ref{fig:WAXS}, produced as described in
-%  \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
-%  since it encodes all structural details down to the sub-nm scale.  
   There are five major features of interest present in the 2D experimental
@@
 	rings along the $z$-axis\cite{feng_scalable_2014}.
-        %meaning if one traces the 
-	%positions of the aromatic rings with a helical curve, then for each full turn 
-	%in the helix, one will encounter two aromatic rings.
 
@@
 	relative intensity.  Accordingly, we name these reflections R-spots. The
-	location of all spots is $\sim$$37^{\circ}$ from the $q_z$ axis in their
-	respective quadrants. In many liquid crystal systems, such spots are explaioned
+	location of all spots is $\sim37^{\circ}$ from the $q_z$ axis in their
+	respective quadrants. In many liquid crystal systems, such spots are explained
 	as the result of alkane chains tilted with respect to the membrane
@@
 	pores.
+
   \end{enumerate}
@@
 	model creates a nanoscopic chemical environment maximally consistent with experiment within 
-	the constraints	of our forcefield. Using this approach, we are able to confirm some previous
+	the constraints	of our force field. Using this approach, we are able to confirm some previous
 	interpretations	of the WAXS pattern and refute others.
-
-	%BJC5: I could add brief references to other LLC studies which look at hexagonal phase, but
-	% without scrutinizing the structural details. In other words, other authors have gotten 
-	% hexagonal phases with self-assembly, but they can't prove that their structure is the same
-	% as experiment. The best there are, are 1D structure factors in the small angle regime.
 
@@
   \end{enumerate}
-
-%  In order to appropriately model transport in these ordered, nanoporous
-%  organic systems, we must first gain a thorough understanding of the nanoscopic
-%  structure of LLC polymer membranes. Our current level of understanding about
-%  the structure at the nanoscale is limited. Using X-ray diffraction and TEM data
-%  we can infer that monomers aggregate into hexagonally packed columns with their
-%  head groups facing towards the column center. There remain several key questions
-%  that we will investigate in order to expand this understanding: 
-%
-%  \begin{enumerate}
-
-%BJC3: reworded a lot of these to be more in line with Matt's way of thinking about LC systems
-%MRS6: formatting suggestion
-%  \item \textit{If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}} 
-%  \item \textit{How many monomers pack around a single pore column?\label{point:monomernum}} 
-%  A simple molecular simulation study of a similar molecule suggested that
-%  4 monomers radially pack around hydrophilic pore columns \cite{zhu_methacrylated_2006}.
-%  Their model likely does not sufficiently imitate the chemical environment present
-%  in the real system since it only contains 16 total monomers. A separate calculation
-%  for NA-GA3C11, based on the estimated volume of the liquid crystal monomers,
-%  proposes that each pore is surrounded by seven
-%  monomers\cite{resel_structural_2000}. Our best chance to answer this question
-%  is by using a molecular model orders of magnitude larger than any other
-%  reported atomistic liquid crystal membrane simulation, as we present here. We
-%  will directly change the density of monomers in each pore and note its effect
-%  on membrane structure.
-%
-%%  \item \textit{How do monomers in each layer position themselves with respect to
-%%  surrounding layers? \label{point:orientation}}
-%  \item \textit{In what orientation do monomer head groups stack on top of each
-%  other \label{point:orientation} 
-%  $\pi$-$\pi$ stacking interactions between aromatic monomer head groups may be
-%  a driving force of self-assembly in this system \cite{gazit_possible_2002}. Gas
-%  phase \textit{ab initio} studies of benzene dimers have shown a clear energetic
-%  advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking
-%  conformations over a sandwiched conformation \cite{sinnokrot_estimates_2002}.
-%  Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking
-%  attraction which favors the parallel displaced configuration in all cases except
-%  where the substitutions are extremely electron withdrawing  
-%  \cite{waller_hybrid_2006,ringer_effect_2006}. We did not consider the T-shaped 
-%  configuration due to its geometric incompatibility with a hexagonal columnar phase.
-%  The entropic contribution of the long alkane tails should overwhelm any attraction
-%  between aromatic head groups in the T orientation. We limit our studies to
-%  comparison of systems built in the parallel displaced and sandwiched configurations.
-
-% BJC3: I don't want to limit X-ray diffraction patterns just to deciding between
-% parallel displaced and sandwiched. Since it doesn't actually decide either way.  
-%  In this study, we
-%  compare simulated X-ray diffraction patterns to experiment in order to deduce
-%  which stacking configuration is most likely. We also dive deeper into the
-%  origin of features present in the 2D diffraction patterns.
-
-%  \item \textit{Does our model support the existence of layers and if so, how well
-%  defined are the layers? \label{point:layers}}
-%  Indications of strong $\pi$-$\pi$ stacking interactions in the direction
-%  perpendicular to the membrane plane, combined with the wedge-like character of
-%  the LLC monomers, suggests that monomers should arrange into disks that stack in
-%  layers. $\pi$-$\pi$ stacking will only occur between the aromatic
-%  monomer head groups which leaves no description of what is happening in the
-%  monomer tail region. The tails may entangle isotropically while maintaining
-%  stacking order among headgroups.  
-% BJC3:rephrasing everything about the above question. 
-%  \item \textit{How strong are stacking correlations between monomer head groups?
-%  \label{point:layers}}
-
-%BJC3: Going to talk about temperature rather than ordered/disordered states
-%  \item \textit{Can the system exist in other metastable states or phases that are not
-%  accessed during experiments? \label{point:metastable}}
-%  There remains the possibility that there is more than one metastable state
-%  associated with a given LLC phase. Simulating a membrane atomistically
-%  requires many atoms which limits the timescales acessible with MD. It is
-%  reasonable to expect that we will generate configurations which are kinetically
-%  trapped in a metastable free energy basin. We must be able to identify which
-%  states 
-  %MRS6: best not to set up too high expectations
-  %is produced experimentally.
-%  are most consistent with experiment.
-
-%  \item \textit{What constitutes a pore, and what are the details of its composition?
-%  \label{point:poredefinition}}
-%  The limited picture that experiment provides tells us that there are
-%  hexagonally packed, hydrophilic regions where transport is likely to occur.
-%  One may instinctively assume that these regions are hollow tube-like pathways.
-%  We will explore the composition of the pores and the partition between the
-%  hydrophilic and hydrophobic regions. 
-% 
-%
-%  \item \textit{Is it necessary to include any water in order to appropriately model
-%  the Col\textsubscript{h} phase? \label{point:water}}
-%  While past work describes the Col\textsubscript{h} phase as dry~\cite{feng_scalable_2014}, 
-%  it has been suggested by experimentalists, in
-%  unpublished communications, that it is likely that neat monomer leaches small
-%  amounts of ambient water. Experimentally, achieving a hexagonal phase with a
-%  completely dry system has proven difficult. If neat monomer sits in ambient
-%  conditions, its color turns from transparent to slightly opaque and a hexagonal
-%  phase forms. Although we will not explore whether water is necessary for
-%  self-assembly, we hypothesize that the hydrogen bonding network formed by the
-%  water may play a role in structuring the pores and holding together the
-%  hexagonal phase. We can look at correlation functions and use simulated X-ray
-%  diffraction patterns to see if there is any meaningful structural difference
-%  between a ``dry'' and ``wet'' system.
-%
-%  \end{enumerate}
-
-  %Once we have addressed all of the above questions, we must show that the 
-  %developed molecular model is consistent with physical observations so that we
-  %can rely on conclusions drawn about structural features characteristic of 
-  %the system.
 
@@
   To bypass the slow self-assembly process, we used a variety of automated procedures 
-  %MRSF: code language is not as important
-  %Python scripts 
-  to assemble monomers
-  into a structure close to one of a number of hypothesized equilibrium configurations
+  to assemble monomers into a structure close to one of a number of hypothesized equilibrium configurations
   (Figure~\ref{fig:build_procedure}).
@@
   \end{figure}
-
-  %BJC7: old
-%  \begin{figure}
-%	\centering
-%	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
-%	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
-%		configuration. (b) A Python script assembles monomers into columns which are duplicated 
-%		and rotated to surround hydrophilic pore centers. (c) We chose to stack twenty monomers
-%		into each column. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
-%  \end{figure}
 
@@
   little effect on the equilibrated structure. However, one should not start them
-  too close or there will be high energy repulsions during early equilibration. We chose a pore radius of 0.5 nm and an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
-  of 4.12 nm for our initial configurations. A sensitivity analysis of both parameters is presented in the 
-  Supporting Information, Section S-\ref{S-section:initial_config_dependence}. The 
+  too close or there will be high energy repulsions during early equilibration. We chose a
+  pore radius of 0.5 nm and an initial pore spacing of 4.5 nm, $\sim$10\% larger than the 
+  experimental value of 4.12 nm for our initial configurations. A sensitivity analysis of 
+  both parameters is presented in the Supporting Information, Section S-\ref{S-section:initial_config_dependence}. The 
   distance between vertically stacked monomers, the xy position of monomers with respect 
@@
   Supporting Information, Section S-\ref{S-section:initial_dbwl}.
-
-%  This is true if initial equilibration is performed with pressure control
-%  If we initially space layers too far apart, they will collapse on each
-%  other while simultaneously slipping in between layers of adjacent pores, which
-%  leads to an artificially thick membrane with pores spaced closely together.
-%  Further details of simulations with layer stacked 10 \AA apart are in the supplemental
-%  information.
 
@@
   of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See Figure 
-  S-\ref{S-fig:stacking} for a detailed illustration of the initial configurations in each mode.
-
-  % BJC5: figure here illustrating parallel displaced vs. sandwiched?
+  S-\ref{S-fig:stacking} of the Supporting Information for a detailed illustration 
+  of the initial configurations in each mode.
 
@@
 
-  %BJC5: moved to supporting info
-  %BJC6: Do you think I should add this back since I used nematic order parameter to
-  % differentiate between ordered/disordered basins?
-  %MRS8: I think this is fine, since it's a relatively standard measure. 
-% \subsubsection{\textit{The nematic order parameter}}\label{method:nematic_order}
-%
-%  We calculated the nematic order parameter for our system in order to
-%  understand the degree of ordering among monomer head groups. Typically, the
-%  nematic order parameter is calculated for nematic liquid crystal systems which
-%  are characterized by unidirectional ordering of liquid crystal monomers. The
-%  preferred direction of monomers is defined by the unit director vector,
-%  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
-%  order parameter, $S$, is defined as:
-%  \begin{equation}
-%	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
-%	\label{eqn:nematic_order_parameter}
-%  \end{equation}
-%  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
-%  In a perfectly ordered system, the molecular axis should be aligned with
-%  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
-%  quantifying the degree of monomer head group alignment between systems. We use
-%  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
-%  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
-%  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
-%  the aromatic head groups. See the Supporting Information for a diagram.
-
   \subsubsection{\textit{Generation of simulated X-ray diffraction patterns}}\label{method:xrd}
 
-  %MRS13: I will talk to Matt about getting the code in GitHub.
   We generated simulated XRD patterns based on atomic coordinates in order to
@@
   film whose pores were oriented perpendicular to the direction of the incident
-  X-ray beam. 
-  %BJC6: Below is the part I'm having a hard time putting into words. 
-  Although the pores are vertically aligned, the crystalline domains are
+  X-ray beam. Although the pores are vertically aligned, the crystalline domains are
   still misaligned with respect to the $xy$ plane. To account for this, we averaged
@@
 
-%BJC12: redundant -- copied from methods
-%  We developed standardized methods of measuring the intensity of reflections of interest
-%  in the experimental and simulated X-ray diffraction patterns presented in this work. Here,
-%  we graphically illustrate the methods used for measuring these intensities.
-
-%  All diffraction patterns are normalized according to R-alkanes and the intensities
-%  of all reflections are reported relative to the intensity of R-alkanes. The region
-%  used to calculate the average intensity of R-alkanes is shown in
-%  Figure~\ref{fig:ralkanes}. The top region is excluded because, in the simulated
-%  patterns, R-$\pi$ intersects with R-alkanes.
-
   We reported the intensities of R-$\pi$ and R-double by recording the maximum values
@@
   appear as half of the $q_z$ value of R-$\pi$.
-
- % We measured the intensity of R-spots by calculating the average intensity
- % within a region selected by visual inspection. We report the average intensity
- % within the regions highlighted in red in Figure~\ref{fig:rspots}.
 
@@
   the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
-  %MRS13: it's confusing to have the same label (R-spots) beneath c and d.  Should be different labels if different data.
   \end{figure}
@@
   approximation of the radius of the phenyl ring plane. 
-  %In this way, we include any instances of 
-  %overlapping electron density which would contribute to R-$\pi$. 
   We calculated the radius as the sum of the longest C-C distance within a phenyl 
   ring (2.8~\AA) and two times the carbon atom electronic radius (0.7~\AA)~\cite{slater_atomic_1964}.
-  %MRSF: specify below what 'here' is.  This graph, this study, this section?
-  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
+  In this study, $g(z)$ is characterized by an oscillatory function with a period equal to the
   average distance between stacked monomers, and an amplitude that decays exponentially
@@
   We also used $g(z)$ to calculate the equilibrated vertical stacking distance between
-  monomers, $d_{equil}$. 
-  %BJC5: in case there is an criticism of this method
-  %The simplest way to do so, would be to Fourier transform
-  %$g(z)$ and extract the highest amplitude frequency of the resulting Fourier series. 
-  %However, the size of our system limits the width of the bins in Fourier space. The bins
-  %are too large to extract a precise value of $\mathit{d}_equil$. Instead, 
-  We fit a decaying sinusoidal function (using \texttt{scipy.optimize.curve\_fit}) to 
+  monomers, $d_{equil}$. We fit a decaying sinusoidal function (using \texttt{scipy.optimize.curve\_fit}) to 
   $g(z)$ of the form:
@@
   well enough to extract a reliable value of L.
-  %BJC5: maybe include plots of these fits in supporting info
-
-% BJC5: I don't plan on showing any 2D correlation functions -- maybe to show swelling
-% of solvated systems.
-
-%  In two dimensions, we observed xy and xz pair distribution functions based on
-%  the center of masses of the aromatic head group rings. For the xy pair
-%  distribution functions, we used a rotated frame of reference. For a given center
-%  of mass, we rotated the coordinates so that the vector created from the center
-%  of mass to the pore center was aligned with the positive x-axis.
-
-  %We gave special
-  %consideration to the xy cross-sections since multiple rings exist in the same
-  %plane located at different vertices of a polygon. We used a rotated frame of
-  %reference to avoid ambiguity in the final pair distribution functions. i
 
@@
   generated with point scatterer placement based on the quenched disorder seen in
-  atomistic simulations. The quenched disorder observed in the atomistic simulations is greater in magnitude than thermal 
-  disorder (See Table~\ref{table:quenched_disorder} in Section~\ref{section:rpi}).
-  %MRSF: How much greater? Be a bit more specific (10% greater?  100x times greater?)
-  This method 
-  %MRSF: specify exactly what of the preceeding is meant by ``this method''
+  atomistic simulations. The quenched disorder observed in the atomistic simulations
+  is up to 8 times greater in magnitude than thermal disorder (See Table~\ref{table:quenched_disorder}
+  in Section~\ref{section:rpi}). This method for simulating time-averaged R-$\pi$ profiles
   assumes that the timescales for large scale rearrangements of the
-  system are much longer than what we can feasibly simulate.
+  system are much longer than what we can feasibly simulate with MD.
 
@@
 
-% BJC5: old
-%  Our simulations best support a model built with 5 monomers per layer based on
-%  the measured equilibrated pore-to-pore distances. To discern the composition of
-%  the monomer layers, addressing question (\ref{point:monomernum}), we ran
-%  simulations of systems created with 4--8 monomers per layer. We built systems
-%  in both the parallel displaced and sandwiched configurations with layers
-%  initially spaced 3.7 \AA~apart. We prepared equilibrated configurations
-%  according to the dry equilibration procedure. The pore-to-pore spacing is stable
-%  in all systems are stable after 400 ns of simulation. Figure~\ref{fig:p2p} shows
-%  the equilibrated pore-to-pore distances for all systems tested. Systems built 
-%  with 5 monomers in each layer equilibrate to a pore spacing that is most consistent
-%  with the experimental value of 4.12 nm derived from SAXS measurements 
-%  (Figure~\ref{fig:SAXS}).
-%  
-%  The remainder of this discussion will focus on the analysis of systems built with
-%  5 monomers per layer. Systems built with 6 monomers per layer have an equilibrated
-%  pore spacing c.a. 0.50 nm higher than experiment. Systems built with 4 monomers per 
-%  layer equilibrate to a pore spacing 0.25 nm lower than experiment. In a sense, all
-%  systems tested are at least metastable, however not all will make physical
-%  sense or fit the experimental profile that we are trying to match. In the limit of
-%  infinite time, all simulations will converge to a single density. It is our 
-%  intention to choose an initial configuration which quickly reaches a monomer density
-%  close to experiment.
-
   Our simulations best support a model built with 5 monomer columns per pore based on
@@
   nanosecond simulated here. For simplicity, we group the systems studied here into the ordered
-  and disordered basins. What we find is that any system where $\mathit{d}=3.7$ \AA~can generally 
-  be characterized as being in a more ordered basin, and any system where $\mathit{d}=5.0$ \AA~can
-  be characterized as begin in a more disordered basin. Generally, when monomers are started further 
-  apart, they stay further apart than systems where monomers are started closer together 
-  (see Table~\ref{table:correlation_length}). Extra space between stacked 
-  monomers give the monomer head groups more rotational freedom. We quantified the ordering of
-  the head groups using the nematic order parameter (see Section S-\ref{S-method:nematic_order}
-  for details of calculation). Disordered basin systems have a lower nematic order parameter 
-  (meaning they are more disordered) than ordered basin systems.
-
-  %MRSF: is there some comment that you can make above about the disordered ones not having many of the structures seen in WAXS to make it clearer that they are not as interesting from the get-go, and provide more details in the follow up sections?
-
-  %MRS7: maybe above say where (i.e.
-what section) it will become clear?
-Or possibly describe them here by order parameter instead of by starting distance, and state the correlation between starting distance and order parameter.
-%    All systems tested are at least metastable on the timescales studied here, however not all 
-%  make physical sense or fit the experimental profile that we are trying to match. In the limit
-%  of infinite simulation time, all simulations will converge to a single density. It is our 
-%  intention to choose an initial configuration which quickly reaches a monomer density close 
-%  to experiment. We believe systems built with 5 columns per pore achieve this goal.
-
-  %MRSF: I',m experimenting with ``columns _around_ each pore'' instead of ``Columns _in_ each pore''. Around makes the geometry a bit more explicit. 
+  and disordered basins. What we find is that any system equilibrated with $\mathit{d}=3.7$ \AA~can generally 
+  be characterized as being in a more ordered basin, and any system equilibrated with $\mathit{d}=5.0$ \AA~can
+  be characterized as begin in a more disordered basin. The extra space between stacked monomers
+  in the disordered basin systems gives the monomer head groups more rotational freedom. We 
+  quantified the ordering of the head groups using the nematic order parameter (see Section 
+  S-\ref{S-method:nematic_order} for details of the calculation). Disordered basin systems have
+  a lower nematic order parameter (meaning they are more disordered) than ordered basin systems. 
+  Generally, when monomers are started further apart, they stay further apart than systems where
+  monomers are started closer together (see Table~\ref{table:correlation_length}). This increased
+  equilibrated stacking distance of monomers in disordered basin systems increases their discrepancy
+  with experimental stacking distances derived from WAXS relative to ordered basin systems 
+  (See section~\ref{section:rpi}).
+
   Systems built with 5 columns around each pore equilibrate to a pore spacing that
@@
   %MRSF: not clear of the disordered ones below are for 5 or 6 columns
-Those in the
-  disordered sandwiched and disordered parallel displaced configurations stack
-  %MRSF: maybe use $\sim$ instead of ca., for consistency?
-  $\sim$~4.87 and 4.94 \AA~apart respectively, which is ca. 1.2~\AA~further apart
-  than suggested by experiment. 5 column-per-pore systems stack, at a maximum,
-  0.9 \AA~further apart than experiment (see 
-  Table~\ref{table:correlation_length}).  The remainder of this discussion will therefore 
-  focus on the analysis of systems built with 5 columns per pore.
-
-% BJC6: I don't think I need to say the following in above paragraph since its all in the methods.
-% Our methodology for calculating equilibrium stacking distance is fully explained in section~\ref{section:rpi}.
-% MRS8: sounds good.  
-%  Relative to ordered basin 
-%  6 column-per-pore systems, the unit cell is elongated in its z dimension and contracted in its
-%  x and y dimensions, however the box volume stays nearly constant in all cases 
-%  (Figure~\ref{fig:box_dimensions}). The system is likely not fully equilibrated and may eventually
-%  rearrange into something that resembles a 5 column-per-pore system. Further investigations 
-%  into this are beyond the scope of this paper.
-
-%  \begin{figure}[!htb]
-%  \centering
-%  \includegraphics[width=\textwidth]{box_dimensions.png}
-%  %MRS7: not really clear from the caption why this is shown.
-%  \caption{When monomers are initially stacked 5 \AA~apart ($\textit{d}=5~\AA~$), the unit cell
-%  expands in the z direction and contracts in its x and y dimensions. The volume remain nearly
-%  constant across all cases. The y dimension box vectors are not included since we use 
-%  semiisotropic pressure coupling which requires that the x and y box vectors change uniformly.}\label{fig:box_dimensions}
-%  \end{figure}
+  Monomers in 6 column-per-pore disordered sandwiched and disordered parallel displaced
+  configurations stack $\sim$~4.87 and 4.94 \AA~apart respectively, which is 
+  $\sim$ 1.2~\AA~further apart than suggested by experiment. 5 column-per-pore systems
+  stack, at a maximum, 0.9 \AA~further apart than experiment (see Table~\ref{table:correlation_length}).
+  The remainder of this discussion will therefore focus on the analysis of 
+  systems built with 5 columns per pore.
 
   \subsection{Simulated XRD comparison to 2D-WAXS data}
-  %MRSF: be consistent on ``Section'' vs. ``section''. Check j chem phys b papers for which one is more correct. 
+
   We can better understand the structure of the system by simulating XRD
   patterns produced from equilibrated MD trajectories (see
-  section~\ref{method:xrd}) and comparing these simulated patters to experiment, addressing
+  Section~\ref{method:xrd}) and comparing these simulated patters to experiment, addressing
   question~\ref{point:xrdmatch} in the introduction. We tested systems built with 5 columns per pore
@@
   with the most unambiguous XRD features, the pore-to-pore spacing
-  and the stacking distance, as described in section~\ref{section:mon_per_pore}.  We generated simulated patterns using the locally
+  and the stacking distance, as described in section~\ref{section:mon_per_pore}. 
+  We generated simulated patterns using the locally
   equilibrated portion of each simulation trajectory (see
@@
   each reflection is described in Section~\ref{method:xrd}.
-  %MRS12: should that be in Methods instead of suporting?  Not sure.
-  %BJC12: moved into methods for now.
 
@@
   \end{itemize}
-
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{c|cccccccccc}
-%  \toprule
-% 		   & \multicolumn{5}{c}{Configuration} \\
-%  \hline
-%           &\multicolumn{2}{c}{}            & \multicolumn{2}{c}{}          & \multicolumn{2}{c}{Parallel} & \multicolumn{2}{c}{Disordered} & \multicolumn{2}{c}{Disordered}         \\
-%           & \multicolumn{2}{c}{Experiment} & \multicolumn{2}{c}{Sandwiched} & \multicolumn{2}{c}{Displaced} & \multicolumn{2}{c}{Sandwiched}  & \multicolumn{2}{c}{Parallel Displaced} \\
-%  Reflection & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) & Intensity & Location ($\AA^{-1}$) \\
-%  \midrule
-%  R-alkanes  & 1.0  & 1.4  & 1.0  & 1.4 & 1.0 & 1.4 & 1.0 & 1.4 & 1.0 & 1.4  \\  
-%  R-spots    & 1.3  & 1.4  & 1.3  & 1.4 & 1.2 & 1.4 & 1.1 & 1.4 & 1.2 & 1.4  \\
-%  R-$\pi$    & 2.8  & 1.7  & 44.0 & 1.4 & 7.7 & 1.4 & 8.4 & 1.4 & 10.1& 1.4  \\
-%  R-double   & 0.9  & 0.85 & --   &  -- & --  & --  & --  & --  &  -- & --   \\ 
-%  \bottomrule
-%  \end{tabular}
-%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
-%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
-%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
-%  does not appear in any patterns, and thus has no measurable intensity.}
-%  \label{table:relative_intensities_300K} 
-%  \end{table}
 
@@
 
-%    \begin{table}[h]
-%  \centering
-%  \begin{tabular}{c|ccccc}
-%  \toprule
-% 		   & \multicolumn{5}{c}{Configuration} \\
-%  \hline
-%             &\multicolumn{2}{c}{}     &            & Parallel  & Disordered & Disordered         \\
-%  Reflection & \multicolumnExperiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
-%  \midrule
-%  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
-%  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
-%  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
-%  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
-%  \bottomrule
-%  \end{tabular}
-%  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
-%  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
-%  than experiment and R-spots reflections that are slightly lower than experiment. R-double
-%  does not appear in any patterns, and thus has no measurable intensity.}
-%  \label{table:relative_intensities_300K} 
-%  \end{table}
-
-  %MRS10: would domain misalignment make a difference in itensity?  I though we decided it wouldnt (it would more broaden?).
-  %You can talk about how you WILL analyze the intensity diffence later on, that it doesn't need to be analyzed here.
-  % MRS4: comments from Matt suggest that domain misalignment shouldn't alone be responsible for 
-  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
-  % Let's talk!
-  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
-  % pores in unit cell, tortuosity (?)
-  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
-  % effects.
-%  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
-%  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
-%  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
-%  maximum at $q_z < 1.5~\AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
-%  rather than 3.7 \AA. R-double does not appear in any of the patterns.
-
-%  We will explore its possible origins and reasons
-%  that it does not appear in our simulated patterns in Section~\ref{section:rdouble}.
-
-  %  This type of pattern is characteristic of a helix~\cite{watson_structure_1953}, as the 
-  %  head groups in the parallel displaced configuration are arranged in a helix.
-
-%  We quantified the numerical discrepancies present when comparing the relative intensities
-%  of each reflection of interest between experimental and simulated patterns. 
-%  Table~\ref{table:relative_intensities_300K} shows the relative intensities of each reflection for 
-%  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
-%  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
-%  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
-%  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
-%  %MRS10: weird transition between these two; it's a result that interrupts the discussion of methods.
-%  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
-%  identified spots based on visual inspection. 
-%  %MRS10: what criteria were used?  Need to provide what was used to make the decision.
-%If the spots were not easily discernible, then the 
-%  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
-%  R-$\pi$, as that is where it appears experimentally. The intensity of R-spots is slightly
-%  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
-%  agrees with experiment. There is no R-double intensity to be measured. %MRS10: specific where no R-double intensity was measured. None of the simulations, correct?
-%Figures are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements. %MRS10: Specify what figures clarify what things.  Also, use active voice in this section.
-
-%  There are clear differences between simulated and experimental results that must be addressed
-%  and justified. We will explore the possible origin of select experimental reflections and form 
-%  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
-%  want answer:  
-%  %MRS10: should the ``why is R-pi in not quite the right place'' be here, to have those sorts of questions more centralized?
-%  \begin{enumerate}
-%	\item What is the origin of R-spots?
-%	\item How can we modify our simulations to account for the discrepancies between the experimental and simulated R-$\pi$ peak.
-%  	\item What is the origin of R-double?
-%  \end{enumerate}
-
-% BJC5: old version
-%  Simulated XRD of the sandwiched configuration shows most all experimental features 
-%  except R-double and R-spots. R-pores and R-alkanes appear in their expected locations. 
-%  R-pores is more intense than experiment, likely because we are simulating a perfect,
-%  infinite hexagonal array. The real system has defects and domain misalignment
-%  which decreases the overall intensity. R-$\pi$ appears with very high intensity and
-%  is shifted down to a lower value of $q_z$ meaning monomers in our model prefer to 
-%  stack farther apart.   
-%
-%  Simulated XRD of the sandwiched configuration contains all experimental
-%  features except for R-double. R-alkanes, R-spots and R-pores appear close to their
-%  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
-%  a $q_z$ value lower than experiment meaning the head groups in our model prefer 
-%  to stack farther apart. 
-%
-%  Like the sandwiched configuration, the parallel displaced configuration creates
-%  a simulated XRD pattern with all major experimental reflections except for R-double.
-%  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
-%  and R-$\pi$ appear, however with a lower intensity
-%  relative to R-alkanes when compared to the sandwiched configuration. R-double
-%  appears due to the parallel displaced aromatic rings. It is a subharmonic of
-%  R-$\pi$ since the nearest vertically stacked head group to any given head group
-%  is $2\times$R-$\pi$~away. 
-%  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
-%  \begin{figure}
-%  \begin{subfigure}{0.3\linewidth}
-%        \centering
-%        \vspace{-0.2em}
-%        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{offset_rzplot.png}
-%        \caption{}~\label{fig:rz_offset}
-%  \end{subfigure}
-%  \begin{subfigure}{0.3\linewidth}
-%        \centering
-%%        \vspace{0.25em}
-%        \includegraphics[scale=0.285]{WAXS_raw.png}
-%        \caption{}~\label{fig:raw_waxs}
-%  \end{subfigure}
-%  \begin{subfigure}{0.3\linewidth}
-%        \centering
-%        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{layered_rzplot.png}
-%        \caption{}~\label{fig:rz_layered}
-%  \end{subfigure}
-%  \begin{subfigure}{0.0544\linewidth}
-%        \centering
-%        \vspace{-4.00em}
-%        \includegraphics[width=\linewidth]{colorbar_seismic.png}
-%  \end{subfigure}
-%%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced.
-Any thoughts why?
-We can discuss in person.
-And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
-%%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
-%%BJC2: Sure, I'll add that to supporting info
-%  \caption{The simulated XRD pattern generated from the equilibrated trajectory
-%	  of the parallel displaced configuration (a) exhibits all major reflections
-%	  present in the experimental WAXS pattern (b). The simulated XRD pattern
-%	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
-%	  all major reflections except R-double.}
-%  \label{fig:XRDsim}
-%  \end{figure}
-
-%  In both simulated diffraction patterns R-alkanes appears in the expected location. 
-%  The location of R-pores is not well-defined in comparison to experiment. In order
-%  to resolve those reflections it would be necessary to simulate a much larger system, 
-%  but that is unnecessary since we can measure pore spacing manually as described 
-%  earlier. R-$\pi$ and R
-
-%  In both the parallel displaced and sandwiched configurations, we noted that
-%  R-$\pi$ appears in a location which corresponds to a real space separation
-%  larger than experiment. We attribute this discrepancy to GAFF's inability to
-%  appropriately model the aromatic interactions which would be necessary to
-%  achieve the correct $\pi$-$\pi$ stacking distance. 
-%  %Systems have been modeled that exhibit the correct stacking distance, however
-%  %they are typically made of planar molecules spanning a large area.
-%  %BJC: I saw a paper like this a long time ago, but failed to save the citation and
-%  % now I am having a hard time finding it again. 
-%  The monomers in our model have bulky tails whose entropic contributions compete
-%  with the $\pi$-$\pi$ stacking interaction energy. There have been efforts to
-%  model systems that contain $\pi$ interactions in a classical mechanical context
-%  using polarizable forcefields \cite{baker_polarizable_2015},
-%  %MRS6: 
-%  but they are significantly more computationally expensive to
-%  reach the time scales required to equilibrate these systems at the present time.
-%  %MRS6: not so relevant below.
-%  %We could
-%  %implement a polarizable force field, however it is likely not worth the extra
-%  %computational cost. If our model proves to be inadequate when simulating
-%  %transport, we will revisit our current choice of forcefield.  
-%
-%  In addition to R-$\pi$ being shifted to lower $\mathbf{q}$ values, a few
-%  factors combine to make the simulated R-$\pi$ reflection visibly more intense
-%  than in the experimental pattern. The simplest reason is that R-$\pi$ and
-%  R-alkanes add together to boost the overall signal at intersecting values of
-%  $\mathbf{q}$. In addition, we observe a much higher maximum intensity within
-%  R-$\pi$. The maximum intensity within R-$\pi$ of the normalized experimental
-%  pattern is 3.1, while the maximum intensity within R-$\pi$ of the normalized
-%  parallel displaced simulated pattern is 32.9. 
-%  %MRS2 10x is really big.
-That seems hard to actually manage .
-.
-.
-I didn't realize it was that big.
-For some reason, I thought it was around 3x.
-If it's that big, how come the 7.4 A reflection isn't big?
-It's not clear to me how this is possible.
-Not clear how the angle averaging obscured this before?
-%  %BJC2 From plots of raw structure factor, it doesn't seem like a normalization issue. It was probably obscured in the original angle averaging because it 
-%  % was averaged with neighboring bins
-%  While direct numerical
-%  comparisons between simulation and experiment aren't necessarily precise due to
-%  underlying assumptions, an order of magnitude difference suggests some
-%  significance. We believe that we see such a high maximum for two reasons: (1)
-%  We are simulating a perfectly aligned system so all X-rays reflected along the
-%  pore axis would add constructively. The crystalline domains in the real system
-%  are not perfectly aligned (See azimuthal distribution in Supporting
-%  Information) which would lead to an overall decrease in the intensity of
-%  R-$\pi$. (2) Our system is more ordered with high correlation between layers.
-%  We will come back to this point further in ensuing discussions.
-%
-%  There is a grid-like pattern near $\mathbf{q}=0$ which appears because the
-%  simulated system shows crystalline character. The grid features along nonzero
-%  values of $q_z$ line up with reflections at $q_z=0$ which indicates positional
-%  correlations between columns in the z-direction. This type of correlation is
-%  expected for a crystalline material. 
-%%MRS6: need some justification for why we are not totally surprised the system is crystalline.
-But is is so crystalline in the x direction?
-The grid spacing is ``crystalline-ish'' in both x and z directions.
-.
-.
-we should talk.
-%If our system met the definition of a
-%  columnar liquid crystalline system, we should observe only weak short-range
-%  z-directional correlation within columns, with no correlation between
-%  columns\cite{chaikin_principles_1995}.
-
   \subsubsection{The location of R-alkanes}\label{section:ralkanes}
@@
 
-%  BJC16: moved to methods
-%  We measured the intensity of R-spots by radially integrating the simulated
-%  diffraction pattern for $1.4~\AA^{-1} < |\mathbf{q}| < 1.57~\AA^{-1}$
-%  (between 4 and 4.5 $\AA$ in real space) and then locating and recording the
-%  intensity of the appropriate peaks in the resulting distribution. Because the
-%  R-spots reflection is difficult to distinguish visually as it appears at the
-%  same $|\mathbf{q}|$ as R-alkanes, we calculate the intensity of R-spots by
-%  assuming that its $q_z$ location should be roughly in line with the
-%  experimental R-double, half the $q_z$ distance of R-$\pi$.
-
   Previous literature has attributed the R-spots reflection in this particular
@@
   respect to the membrane plane. We found that it equilibrates to an average tilt
-  angle of -2\degree~(Figure~\ref{fig:tilt}), 
-  %MRSF: any uncertainty analysis for the 2% that can be included?
-  far from the 37\degree~tilt angle
+  angle of -2 $\pm$ 13\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle
   previously used to explain R-spots. Even when we placed position restraints on
@@
   The position, shape, and intensity of R-$\pi$, generated from simulations at
-%  300K, are qualitatively similar to experiment, but have significant
-%  quantitative differences. 
-% BJC12: I don't think I agree that they are qualitatively similar either. The
-% simulated qr cross-sections are spikey and too low (which is qualitatively
-% evident when you look at the simulated XRD patterns)
   300 K have qualitative and quantitative differences from experiment.
@@
 
-%  The difference in intensity ranges from 3 times too high in the ordered parallel
-%  displaced system to 15 times too high in the ordered sandwiched configuration 
-%  (Table~\ref{table:relative_intensities_300K}).
-
   \subsubsection*{Distance and correlation between stacked monomer head groups}
@@
   functions, $g(z)$, as described in Section~\ref{section:correlation_length}.
-  %BJC11: Below is in methods but might be worth restating here? 
-  %MRS12: no, OK here.
-%  based on the center of mass of each monomer head group. In order
-%  to calculate $g(z)$, we averaged all $z$-slices of the 3D pair distribution function, $g(x, y, z)$, 
-%  (Equation~\ref{eqn:correlation}) within
-%  2.1 \AA~of $g(0, 0, z)$. In this way we are measuring correlation between head 
-%  groups within the same column. 
   The resulting distributions are generally characterized by decaying
@@
   greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
-  basins at the high end of that range.% and are on average 0.2 and 0.3 \AA~more distant.
+  basins at the high end of that range.% and are on average 0.2 and 0.3 \AA~more distant. (wording confused Matt)
   This behavior is not surprising since GAFF models atoms as point charges and
@@
   necessarily more tightly packed configuration. To test the this chain-packing hypotheses, 
-  we equilibrated the
-  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
+  we equilibrated the system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
   into a more tightly packed configuration. Before annealing and in order to
@@
   agreement with experiment (Table~\ref{table:correlation_length}). 
-  %BJC11: below might confuse the reader
-%  Note that its correlation length
-%  ($L$ = 14.5 \AA) is larger than what we would expect by inverting the FWHM of the $q_z$
-%  cross-section of R-$\pi$ shown in Figure~\ref{fig:sim_zsection_fit} ($L$ = 1 / 0.163 
-%  = 6.1 \AA). The reason is likely a combination of artificial broadening caused by the
-%  overlap of R-alkanes and R-$\pi$ as well as uncertainty in the fit due to low simulated
-%  XRD resolution.
   We could not extract a reliable correlation length from the disordered
@@
 
-  %BJC11: trying to figure out how to communicate distance correlation
-  % wikipedia's explanation of distance correlation makes it seem like we are using it right:https://en.wikipedia.org/wiki/Distance_correlation
-  % could say "distance covariance"
   Overall, we believe our simulations exhibit a realistic amount of distance
@@
 
-% BJC9: old version of above paragraph
-%  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
-%  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
-%  The FWHM of the $q_z$ cross-section is 76\% larger than experiment and the
-%  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
-%  experimental data is best fit with a Lorentzian function while the simulated
-%  patterns are best fit using a Gaussian function. The simulated spectra do not
-%  incorporate the effects of finite domain sizes, pressure broadening and
-%  instrumental broadening which would alter the peak shape. In the absence of
-%  these and other peak broadening effects, the experimental peak would actually
-%  be narrower, further increasing the discrepancy with simulation.
-
-% BJC11: paragraph seems unnecessary
-%  We have identified a number of potential ways that simulation conditions,
-%  forcefield and initial configurations could affect the intensity and shape of
-%  R-$\pi$, and we assessed each using a simplified model of the pores. Our simplified model 
-%  represents each monomer head group as single point scatterers and places them in either
-%  a parallel displaced or sandwiched configuration. We chose to explore the 
-%  influence of thermal noise in each dimension, the effect of $z$-direction 
-%  distance correlations between scatterers within columns, as well as correlation
-%  between columns since these are the variables we believe have the largest 
-%  influence on peak shape and intensity.
-
   We studied the shape and intensity of R-$\pi$ by setting up simplified
@@
   production simulations.
-  %We hypothesize that, experimentally, the quenched disorder is the 
-  %same as thermal disorder, but we cannot reach the necessary transition
-  %timescales to fully thermalize in these simulations.
 
@@
 
-  %MRS10: somewhere in here, we need to address whether thermal and quenched disorder are 
-  % the same experimentally. If not the same, then it's glassy, if they are the same, then 
-  % we are making the assumption that the the timescales of motion of that noice are > 1 microsecond but < 1 second.  
-  %BJC11: most of this section moved to methods.
-%  We can study the shape and intensity of R-$\pi$ using a simplified baseline model
-%  which has the same amount of disorder present in our atomistic simulations. For these
-%  models, we represent each monomer as single point scatterers located at the center of mass of
-%  each monomer head group, and place them in a configuration spatially similar to those
-%  seen in our simulations. We made them 4 times taller in the $z$-direction in order to access
-%  higher $q_z$ resolution. When placing points, there are two sources of disorder to consider: 
-%  thermal motion of atoms and quenched disorder which is created by rapid structural 
-%  rearrangement during early equilibration and is largely locked into place for the remainder
-%  of the simulation. We measured thermal disorder by calculating the standard deviation of 
-%  the distribution of head group center of mass positions from their average positions. We 
-%  measured quenched disorder by calculating the standard deviation of the distribution of head
-%  group center of masses from their idealized average positions. In the $z$-direction, we
-%  measured the deviation of the head group center of masses from an equally spaced column
-%  of head groups. In the $xy$ plane, we calculated the standard deviation in radial position
-%  from the pore center and the angular deviation from equally spaced points surrounding 
-%  the pore center. This method for calculating quenched order inherently includes thermal 
-%  disorder. The values measured for each system and type of disorder are given
-%  in Table~\ref{table:quenched_disorder}. The magnitude of quenched disorder is greater than
-%  thermal disorder.
-
-  %BJC11: moved a variation of this to methods
-%  To avoid any dependence on initial configuration, we calculated the average R-$\pi$
-%  profile using simple system trajectories of 1000 independent configurations. We
-%  determined the amount of disorder to add to each independent configuration using
-%  the values for quenched disorder given in Table~\ref{table:quenched_disorder}.
-
-  %MRS10: this is more of a methodological thesis than is ideal. Can you make it more about what we are learning, or at least what was done and the reasoning?  
-%  The expected maximum intensity of R-$\pi$ can be calculated from a single
-%  trajectory of uncorrelated configurations rather than from the average of 
-%  multiple trajectories of correlated frames. Theoretically, in order to
-%  mimic the simulated system, we should build an initial configuration which 
-%  has the same amount of quenched disorder as our simulations and then create
-%  a trajectory to which we add thermal noise to each subsequent frame. In this
-%  scenario, the positions of each scatterer will not change in a way that 
-%  significantly affects the intensity of R-$\pi$ since most of its character 
-%  is defined by the far more disordered initial configuration. To uncover the
-%  expected intensity of R-$\pi$, we would need to average over many such 
-%  trajectories. To bypass this expensive calculation, we instead calculate the
-%  R-$\pi$ intensity from a trajectory consisting of many independent initial 
-%  configurations. This simulates the long time scales over which we expect 
-%  columns to sample many configurational states. %We use the latter method 
-%  %for the remainder of this section since we can extract the trends we 
-%  %need using a single trajectory at a fraction of the computational cost.
-
-% BJC11: I eliminated this figure and the discussion of distance correlation between
-% scatterers since the only real issue with the qz cross-section is the intensity. 
-% I explain how we create correlated distances in the methods. We weren't really 
-% showing anything new since correlation length equal 1 / FWHM_qz
-%  \begin{figure}[!htb]
-%  \centering
-%  \begin{subfigure}{0.3\textwidth}
-%  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
-%  \caption{}\label{fig:sf_qy_nocorrelation}
-%  \end{subfigure}
-%  \begin{subfigure}{0.3\textwidth}
-%  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
-%  \caption{}\label{fig:sf_qy_correlation}
-%  \end{subfigure} 
-%  \begin{subfigure}{0.3\textwidth}
-%  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
-%  \caption{}\label{fig:sf_qz_correlation}
-%  \end{subfigure}   
-%  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
-%  points meant to represent monomer head groups. We added a similar amount of noise to 
-%  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
-%  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
-%  peaks. (b) When we correlate the distance between points within each column, the 
-%  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
-%  intensity between the center and outer peaks. (c) Correlation of the distance between
-%  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
-%  \end{figure}
-
-%  The $q_r$ and $q_z$ profiles of R-$\pi$ generated from a simplified parallel displaced trajectory
-%  where we represented monomer head groups with point scatterers exhibits sharp peaks with
-%  no breadth. Figure~\ref{fig:sf_qy_nocorrelation} and~\ref{fig:sf_qz_correlation} shows
-%  the $q_y$ and $q_z$ cross-sections of R-$\pi$ generated by simulating the structure 
-%  factor of the trajectory. The distance between peaks in the $q_y$ cross-section is 
-%  equivalent to the distance between pores in real space.
-
-  % BJC11: probably unnecessary discussion. Could add to supplemental.
-%  Correlation between scatterers increase the intensity of R-$\pi$ and broadens
-%  its $q_z$ cross-section. In the simplified system described above, we added
-%  Gaussian noise to the mean positions of an equally spaced column of points. 
-%  This ignores any interaction head groups might have with each other. To remedy
-%  this, we placed points in the $z$-direction by drawing random samples from a
-%  multivariate normal distribution defined by the mean positions of an equally
-%  spaced column of points. We gave the distribution at each point along the column
-%  the same standard deviation, $\sigma_z$, shown in Table~\ref{table:quenched_disorder}.
-%  We defined a covariance matrix such that the covariance, $v$, of the distance, 
-%  $d$, between scatterers decays exponentially from $v$ according to the equation
-%  $ve^{-d/L}$, where $L$ is the correlation length. We simulated the structure
-%  factor of a simple system built as described above with a correlation length of
-%  30 $\AA$. We chose 30 $\AA$ in order to exaggerate the effect of correlation
-%  length for visual purposes. Subsequent structure factor calculations are all
-%  done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section
-%  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$
-%  cross-section (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in
-%  experiment. Additionally, there is a near 20\% increase in the maximum
-%  intensity of R-$\pi$ when the distances between scatterers are correlated.
-
-  %BJC8: Can show correlation effect on intensity in supporting info
-
-% BJC9: omitted because these are not strong points
-%  The peak height
-%  indicates the degree of local ordering and influences the intensity of R-$\pi$.
-%  If vertically adjacent sandwiched head groups were less ordered, which might be
-%  achieved with much longer simulations, then the leading peak intensity should
-%  decrease and the correlation length would increase. We expect that the leading
-%  peak would only get more intense if monomers stacked 3.7 \AA~apart. Conversely,
-%  parallel displaced head groups are not as confined by their vertically adjacent
-%  neighbors. This z-direction translational freedom may still be feasible if
-%  monomers stack 3.7 \AA~apart in a parallel displaced configuration, meaning the
-%  system would maintain a correlation length and R-$\pi$ intensity in relative
-%  agreement with experiment.
-
   Increasing thermal noise in the $z$-direction will reduce the intensity
@@
   \end{subfigure}
-  #MRSF: yellow not legended?
+  %MRSF: yellow not legended?
   \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
@@
   background intensity, relative to systems with simulation levels of disorder (blue)
-  %as seen in simulation (blue) 
-  by a factor of 3 when we
-  increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase
-  $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
+  by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor 
+  of 15 when we increase $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
   decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
@@
   creating a simplified sandwiched configuration (as described above), 
-  with varying amounts of statistical correlation between columns (see Figure~\ref{fig:column_displacement}). In the low independent motion limit
+  with varying amounts of statistical correlation between columns 
+  (see Figure~\ref{fig:column_displacement}). In the low independent motion limit
   limit, the COM of columns are situated at the same $z$-coordinate.
@@
   %MRSF: I had a bit of hard time connecting the thesis of this paragraph to the details provided.
-  It therefore seems likely that the discrepancy between the intensity of
+  %BJCF: tried reorganizing a bit
+  It therefore seems likely that the discrepancy between the shape and intensity of
   R-$\pi$ generated from our simulations versus experiment is primarily due to
-  highly correlated columns in our initial configurations, likely due to the
-  highly symmetric starting configuration. If the columns were uncorrelated,
-  $g(z)$ of the ordered sandwiched system would very closely resemble
-  Figure~\ref{fig:z_correlation_sandwich} when we average all $z$-slices of the
-  3D correlation function. When we include all $z$-slices in $g(z)$ for our
-  system, rather than restricting it to those $z$-slices within 2.1~\AA of the
-  center of the correlation function (Section~\ref{section:correlation_length}),
-  the function shows oscillatory behavior and the correlation length
-  nearly triples to 12.4 $\pm$ 0.7 \AA. (Figure~\ref{fig:z_correlation_fullbox}).
-  Since all columns in our initial configuration are started at the same
-  $z$-coordinate, $g(z)$ on average exhibits correlation of head groups with
-  other head groups within the same column, with head groups in other columns
-  within the same pore, and with head groups in different pores.
+  highly correlated columns in our highly symmetric initial configurations.
+  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
+  would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
+  average all $z$-slices of the 3D correlation function since contributions to
+  $g(z)$ from head groups in other columns within the same pore, and with head
+  groups in different pores would cancel out. However, when we include all 
+  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
+  $z$-slices within 2.1~\AA of the center of the correlation function 
+  (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
+  behavior with a correlation length that nearly triples to 12.4 $\pm$ 0.7 \AA.
+  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
+  reinforced by head groups in neighboring columns which is not expected
+  in a system where columns act independently.
+  %Since all columns in our initial
+  %configuration are started at the same $z$-coordinate, $g(z)$ on average exhibits
+  %correlation of head groups with other head groups within the same column, with
+  %head groups in other columns within the same pore, and with head groups in different pores.
 
@@
   that the radial ordering of the head groups may benefit from further optimization.
-  %MRS12: is there a structral 
-  %implicatiob to the above?  It should be given explicitly so readers see where it fits in the story .
-  % It could be that there is no real structural implication, which is fine, as long as its explicitly stated. 
-  %is q_r cross-section right in experiment?  Does this explain differences our simulations would need to have? 
-  %BJC12: There are structural implications - namely that if the pore region had 
-  % more disordered head groups, then R-pi would sharp. If they were more ordered, it
-  % would get wider. But our fits show similar FWHMs. Even though the fit isn't 
-  % great, I don't think we can say one way or the other. But once we fix everything
-  % else, maybe that's something we could look at.
 
@@
 
-% BJC15: this paragraph reframed and expanded below
-%  Because disorder among head groups in the simulated 
-%  atomistic systems is largely determined by each system's quenched configuration,
-%  one would need to average an ensemble of simulations in order to optimally match the experimental WAXS pattern. 
-%  Both the initial configuration and initial velocity randomization lead to 
-%  different quenched configurations every time we run an equilibration simulation.
-%  Although the simulated XRD pattern changes dynamically as we simulate the system
-%  due to thermal fluctuations, its features are largely determined by the initial 
-%  quenched configuration. Here we assume that the timescales for large scale 
-%  rearrangements of the system are much longer than what we can feasibly simulate.
-
   \subsubsection*{Quenched disorder in ensembles of configurations}
 
-%MRSF: suggest breaking up this paragraph into 2-3 paragraphs.
-Thesis is just that we studied ensembles of short simulations,but would be clearer stronger of some of the results are separated out into their own paragraph.
-
-  Since the dynamics of this system are slow, and consequently most
-  of our analysis has been focused on a set of quenched configurations
-  with some structural characteristics that do not vary significantly
-  with time, we attempted to learn more about their time-averaged 
-  structures by studying ensembles of shorter simulations started
-  from more independent initial configurations. We created ensembles
-  of 40 simulations in both the parallel displaced and sandwiched 
+  Since the dynamics of this system are slow, and consequently most of our analysis
+  has been focused on a set of quenched configurations with some structural 
+  characteristics that do not vary significantly with time, we attempted to learn
+  more about their time-averaged structures by studying ensembles of shorter 
+  simulations started from more independent initial configurations. We created
+  ensembles of 40 simulations in both the parallel displaced and sandwiched 
   configurations. We used the same equilibration scheme as above 
-  (see Section~\ref{section:equilibration}). However, we built the 
-  initial configurations with randomly displaced columns in the 
-  $z$-direction and looked at the results after 5 ns of unrestrained
-  simulation, which should capture any quenched disorder built in 
-  from the initial configurations. We then simulated XRD patterns 
-  from the 40 trajectories, concatenated together. The $q_r$ 
-  cross-sections of R-$\pi$ generated from the two concatenated 
-  trajectories are shown in Figure~\ref{fig:ensemble_XRD}. 
-%MRSF: maybe here break?  might need a bit of rephrasing of thesis.
-  Qualitatively, the cross-sections of are nearly smooth, with only
-  small spikes near $q_r$=0. These data suggest that the average 
-  intensity of R-$\pi$ in the ensemble of sandwiched systems is 
-  about 3$\times$ higher than that in the ensemble of parallel displaced
+  (see Section~\ref{section:equilibration}). However, we built the initial 
+  configurations with columns randomly displaced in the $z$-direction and looked at
+  the results after 5 ns of unrestrained simulation, which should capture any 
+  quenched disorder built in from the initial configurations. We then simulated
+  XRD patterns from the 40 trajectories, concatenated together. The $q_r$ 
+  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
+  in Figure~\ref{fig:ensemble_XRD}.
+
+  Qualitatively, the $q_r$ cross-sections of R-$\pi$ generated from ensembles of
+  simulations are nearly smooth, with only small spikes near $q_r$=0. These data
+  suggest that the average intensity of R-$\pi$ in the ensemble of sandwiched 
+  systems is about 3$\times$ higher than that in the ensemble of parallel displaced
   configurations. Compared to our long simulations, the intensity of R-$\pi$
@@
   and by a factor of 2 for the sandwiched and parallel displaced configurations respectively.
-  %MRS16: probably don't want to talk about which combination BEST agrees with the ensemble,
-  %but present the different things that in combination would explain most of the differences.
-%MRSF: maybe split here?  Not sure, but definitely some split.
+
   Overall, the intensity of R-$\pi$ generated from the parallel displaced 
@@
   we will limit the following discussion to the parallel displaced configuration.
-  Equivalent data is available for the sandwiched configuration in the
-  supporting information. %BJC15: to be added
-  %MRSF: add section number here, consistency on capitalization?
-  %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
-  % However, I can switch it to sandwiched very easily. The discussion below will remain the same
-  %MRS15: I think better to just talk about how much things can be reduced in height.
-If there are OTHER features that look more characteristic of the experiment in parallel displaced, you can talk about those.
+  Equivalent data for the sandwiched configuration is presented in Section 
+  S\ref{S-section:sandwiched_ensemble}.
 
@@
   \end{subfigure}
-  %MRSF: explicitly refer to the previous graph that this is ``much smoother'' than.
-  \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
-  		   patterns from an ensemble of 40 independent simulations, suggesting that much of the extra initial intensity may be due to the starting conditions. The maximum 
-  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
-  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
+  \caption{The $q_r$ section of R-$\pi$ is much smoother than~\ref{fig:sim_rsection_fit} when
+  		   we generate simulated XRD patterns from an ensemble of 40 independent simulations,
+  		   suggesting that much of the extra initial intensity may be due to the starting 
+  		   conditions. The maximum intensity of R-$\pi$ is 3$\times$ higher in the sandwiched
+  		   configuration (a) than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
   \end{figure}
@@
 I think also this paragraph should be split up more to emphasize findings.
-  These short independent simulations exhibit similar amounts of quenched disorder. 
-  We pooled the deviations of each head group COM from idealized positions
+  These short independent simulations exhibit a symmetric distribution of quenched
+  disorder. We pooled the deviations of each head group COM from idealized positions
   from all independent simulations in order to create the distributions shown in 
-  Figure~\ref{fig:offset_ensemble_pooled} 
-  (see Section~\ref{method:simple_systems}). The distributions appear 
-  symmetric meaning that there is an equal chance for a head group to displace
-  in the positive or negative $z$, $r$, or $\theta$-direction. We verified that
-  this is the case for individual COMs. 
-  % For a given system, there are 400 head groups. 
-  If we consider the COM of a given head group, we expect that the
-  distribution of its deviations from its idealized position among all the 
-  independent simulations
-%  the $z$, $r$, and $\theta$ directions 
+  Figure~\ref{fig:offset_ensemble_pooled} (see Section~\ref{method:simple_systems}).
+  The distributions appear symmetric meaning that there is an equal chance for a head
+  group to displace in the positive or negative $z$, $r$, or $\theta$-direction.
+
+  We verified that this same symmetry exists when looking at individual COMs.
+  If we consider the COM of a given head group, we expect that the distribution of
+  its deviations from its idealized position among all the independent simulations
   should be symmetric about its idealized position. We can calculate the 
-  empirical cumulative distribution function (ECDF) 
-  of these distributions of deviations. 
-  % Each ECDF contains 40 data points, one from each independent simulation.
-  The ECDFs of 3 randomly selected COMs
-  are shown in Figure~\ref{fig:offset_ecdfs} to guide the eye (colored lines). The average 
+  empirical cumulative distribution function (ECDF) of these distributions of 
+  deviations. The ECDFs of 3 randomly selected COMs are shown in 
+  Figure~\ref{fig:offset_ecdfs} to guide the eye (colored lines). The average 
   of all COM ECDFs is represented by the red line with the 95\% confidence
@@
   \begin{subfigure}{\textwidth}
-  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
-  %MRS15: 95% is fine.
   \includegraphics[width=\textwidth]{offset_ecdfs.pdf}
@@
 
-  %MRS10: Maybe rephrases; rather than talking about building a better
-  %model, you can summarize the differences that could explain the discrepancy between experiment and simulation.
-  %BJC11: tried above.
-%  We can use what we learned above in order to construct a better model,
-%  however there will still be shortcomings. In order to make head groups stack
-%  closer together, we can adjust the force field parameters for aromatic 
-%  carbons.  We can decrease the intensity of R-$\pi$ if we incorporate more
-%  $z$-directional noise, which may come from increasing the system's temperature.
-%  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
-%  % temperature? Is decreasing the force constant between bonds viable? 
-%  We can also decrease the intensity of R-$\pi$, in addition to smoothing the
-%  $q_y$ cross-section by creating initial configurations whose columns are
-%  displaced randomly in the $z$-direction. We can achieve better averages if we
-%  create systems with more pores in the unit cell. Ultimately, we will need extremely
-%  long simulation times, or enhanced sampling techniques so that monomers within
-%  columns can rearrange and sample enough independent configurations to generate
-%  a robust simulated XRD pattern.
-
   \subsubsection{Origin of R-double}\label{section:rdouble}
@@
   without the inclusion of small amounts of water in the pores.
-
-%  There is no way to produce R-double without a more complex initial configuration. We 
-%  calculated the structure factor of simple idealize systems with points representing monomer
-%  head groups that mimic 
-%%BJC6: reference atlas of optical transforms. Get rid of idealized systems in supplemental
-%  displaced and sandwiched configurations. Neither give rise to R-double. 
-%  (See section S~\ref{S-section:simplified_assemblies}). The appearance of R-double implies a
-%  vertical modulation in electron density every 7.4 \AA. It is possible that this modulation 
-%  occurs in either the head or the tails. It is also possible that R-double does not appear in
-%  a completely dry system. We will address this point in section~\ref{section:water}.
 
@@
 
-    %BJC10: I think this belongs somewhere in this section.
-    %BJC11: might be covered well enough in above 
-%  The simulated XRD patterns of the parallel displaced configurations show additional
-%  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
-%  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
-%  for the same reason as R-double. It is possible that parallel displaced monomers contribute
-%  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.
-
-% BJC6: removed to cut down on amount of material. This one is the biggest stretch in my opinion.
-%MRS12: I think it is useful to put in just to show we've been thinking about them.  Can omit the figure in the main text.
   One way to produce R-double is if our initial configuration contains
@@
   possible overestimates of the barrier height in the classical force field.
-%  
-%  %BJC5: add citation for extended pi conjugation
-%  There are instances where carboxylate groups in other systems rotate out of plane. Bushey et
-%  al. showed that bulky carbonyl-containing substituents of stacked arene molecules tended to
-%  tilt 45$\degree$ in order to relieve steric strain, thus allowing $\pi$-$\pi$ stacking between 
-%  molecules, and to hydrogen bond with neighboring molecules. Lorenzo and Gra\~{n}a found 3
-%  stable dimers of gallic acid (from which the monomer, Na-GA3C11 is derived) with adenine. In
-%  all cases, the carboxylate group remained planar, even with evidence of hydrogen bonding
-%  between the carboxyl group and nitrogen atoms of adenine. The monomers which we are studying
-%  have no opportunities to hydrogen bond and are confined so that any rotation about the phenyl--
-%  carboxylate bond would be sterically hindered.
 
@@
   stable for a few nanoseconds and R-double quickly fades.
-  %MRS12: seems like unnecssary speculation below, since there are a lot of cancelling affects. 
-  %The long-term stability of a configuration similar to this may be feasible if monomers stay
-  %stacked 3.7 \AA~apart.
 
@@
   (Figure~\ref{fig:staggered_rzplot_norestraints}). 
-  %MRS12: not sure this is necessary.
-  %To our knowledge, there have been no
-  %studies that specifically address the possibility of a configuration like this.
   Our force field causes our system to tend towards uniformly spaced layers.
@@
   an answer to question~\ref{point:water} posed in the introduction.
-%  through the creation of shared hydrogen bonds between water molecules and carboxylate
-%  groups of vertically stacked monomers. 
   We added water to the parallel displaced and sandwiched configurations in the
@@
   detail in the Supporting Information, Section S-\ref{S-section:rdouble}.
-
-%BJC12: move to supplemental
-%  shown in Figure~\ref{fig:pore_hbonds}. 
-%  In order to create Figure~\ref{fig:pore_hbonds}, we binned the $z$-positions of the
-%  center of mass of the monomer head groups into 20 bins, the same number as the monomers
-%  per columns. This works relatively well since there is a high degree of correlation between
-%  columns in our system. Peaks in the distributions represent the scenario where a monomer head group
-%  shares a water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
-%  we calculated the discrete Fourier transform of the distributions which we used as a rough 
-%  indicator of whether the head group arrangement will lead to R-double. We see the 
-%  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 
-%  0.75 $\AA^{-1}$ are clearly distinguishable, meaning there is periodicity at twice
-%  the $\pi$-stacking distance.
 
@@
   \centering
-  % BJC6 : below is the simulated diffraction pattern of the full system. I removed it since showing both
-  % makes both patterns small. You can see the full pattern in a separate figure.
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}  
-%  \end{subfigure}
   \begin{subfigure}{\textwidth}
@@
   \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{pore_hbonds.png}
-%  \caption{}\label{fig:pore_hbonds}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
-%  \caption{}\label{fig:pore_hbonds_ft}
-%  \end{subfigure}
   \caption{(a) The structure of the head groups is responsible for the appearance of
@@
   together in the $z$-direction. Blue monomers were stacked above orange monomers in the
-  initial configuration. 
-  %MRS12: I think subfigure C can be moved to supporting, and we just desribe the alternating structure in the text.
-I think %it's likely to be too confusing for many readers as a figure, and takes up too much space.
-%(c) We group the $z$-coordinate of the center of mass of monomer
-%  head groups into 20 bins. Peaks in the distributions indicate a shared hydrogen bonded
-%  water molecule between a monomer head group and one in the bin vertically above it. 
-%  The distance between the peaks roughly corresponds to the distance between pairs of 
-%  monomers. The distance between peaks in pore 1 (indicated by arrows) is equal to two 
-%  times the $\pi$-stacking distance. In this scenario, monomers are no longer evenly spaced
-%  in the $z$-direction since they are pulled closer together by hydrogen bonds. (d) We 
-%  performed discrete Fourier transforms on each distribution in (c) In Pore 1, there 
-%  also periodicity every 8.3 $\AA$, twice the $\pi$-stacking distance, as indicated by the
-%  intensity at 0.76 $\AA^{-1}$. In this case, the center of mass of two adjacent pairs 
-%  is separated by twice the average monomer stacking distance, while the four monomers 
-%  involved are unequally spaced. These conditions seem likely to give rise to R-double.
-  }\label{fig:hbonds}
+  initial configuration.}\label{fig:hbonds}
   \end{figure}
@@
   a separation process. We aim to further understand the pore architecture, in
-  order to address question~\ref{point:composition} postedd in the introduction, and observe the differences,
-  if any, between the different plausible equilibrated configurations studied so far.
-
-  %MRSF: seems like a thesis w/o supporting data - maybe merge paragraphs, or provide a survey of the findings presented below.
-  %BJC6: moved this paragraph up to make the section more idea-focused
-  In general, the composition of each region, particularly within our
+  order to address Question~\ref{point:composition} posted in the introduction, 
+  and observe the differences, if any, between the different plausible equilibrated
+  configurations studied so far. In general, the composition of each region, particularly within our
   definition of the pore region, is similar between all systems. This suggests
@@
   differences between different possible structures studied here.
-  %We believe we can solvate and study transport
-  %in any of the systems presented here and extract similar transport mechanisms. We will 
-  %need to verify that this assumption is true.
+
+  %MRSF: seems like a thesis w/o supporting data - maybe merge paragraphs, or provide a survey of the findings presented below.
+  %BJC: merged above
 
@@
   region, we used carbon atoms of the monomer tails (See Figure S-\ref{S-fig:monomer_color_coded}
-  of the Supporting Information for a diagram). We averaged the histograms over at least 50 ns of equilibrated trajectory.
-  %MRSF: why 50 ns? 
+  of the Supporting Information for a diagram). We averaged the histograms over the equilibrated
+  portion of the trajectory. 
   There is a gradient in pore composition transitioning radially from the hydrophilic 
@@
   experiments, the pore radius was estimated to be 0.6 nm~\cite{zhou_supported_2005}. 
-  %MRSF: see before by 'we'.  You mean previous studies? Tried to tweak.
-  %MRS13: be more clear.  ``We define'' would imply from THIS study, but I think you are just talking about other studies.
-  %BJC5 : Add vertical line to plots for 'pore radius'? Might be too busy.
-  %MRS8: I actually think it might add understanding  I would label it as ``experimentally estimated size-exclusion radius''.
   However, the simulations do not confine
@@
 
-%  These observations bring into question how
-%  one should define a pore in these types of systems. One usually measures a 
-%  membrane's pore radius based on the size of a molecule it can reject, however
-%  it is not clear where the edges of the pores are and what size molecule would
-%  fit through. We leave these investigations for a future study.
-  %MRS7: or could say that the size could be different depending on the the nature of the molecule. Could bring up
-  %Sarah's results with different selectivity of molecules about the same size.
-
   The space in the pore region is filled with a mixture of sodium ions
@@
 
-  %BJC6: redone with only tops of histograms plotted, and water added
-  %MRS8: this is good at showing most structures are the same.
-It would be nice to also see how different components relate to each other spatially.
-Perhaps you can add a picture (can pick just one, since they are so similar) and plot the different components on one plot to show how the gradients intersect.
   \begin{figure}[!htb]
@@
   \end{figure}
-
-%  \subsection{The Effect of Water on Structure}\label{section:water}
-%
-%  %MRS7: generally good data, we should talk about how to tighten it up. For example, thesis shouldn't be 
-%  % a history of what we did. 
-%  We explored the effect of water on pore structure, addressing question
-%  (\ref{point:water}), by preparing parallel displaced and sandwiched
-%  configurations according to the wet equilibration procedure. We limit
-%  the discussion to the ordered pore basin since it produces the most experimentally
-%  consistent equilibrated configurations. There is no experimental measurement
-%  of trace water concentration in these membranes so we tested a range of water
-%  concentrations from 1\% to 5\%. Figure~\ref{fig:solvation} shows the simulated
-%  diffraction patterns resulting from each configuration.
-%  
-%  % formatting taken from : https://tex.stackexchange.com/questions/239715/add-titles-for-rows-and-columns-in-a-subfloat
-%  \newlength{\tempdima}
-%  \newcommand{\rowname}[1]% #1 = text
-%  {\rotatebox{90}{\makebox[\tempdima][c]{\textbf{#1}}}}
-%  
-%  \renewcommand{\thesubfigure}{\alph{subfigure}}
-%  \newcommand{\mycaption}[1]% #1 = caption
-%  {\refstepcounter{subfigure}\textbf{(\thesubfigure) }{\ignorespaces #1}}
-%  
-%  \begin{figure}[!htb]
-%  \begin{subfigure}{0.915\textwidth}
-%  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
-%  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
-%  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
-%  	\rowname{Parallel Displaced}&
-%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
-%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
-%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_5.png}\\[-1ex]
-%  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
-%  	\rowname{Sandwiched}&
-%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_1.png}&
-%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
-%  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_5.png}\\[-1ex]
-%  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
-%  	\end{tabular}
-%  \end{subfigure}
-%  \begin{subfigure}{0.075\textwidth}
-%  	\includegraphics[width=\textwidth]{colorbar_jet.png}
-%  \end{subfigure}
-%	\caption{Adding 1 wt\% water to the ordered basin dry systems causes an increase in the intensity
-%	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
-%	of water increase discrepancies with experiment} %MRS7:by increasing disorder?
-%  \label{fig:solvation}
-%
-%  \end{figure}
-% 
-%  The addition of water %allows 
-%  results in R-double to transiently appear. When we add 1 wt\% water to the 
-%  parallel displaced configuration, R-double becomes visible (Figure~\ref{fig:rdouble_offset}). 
-%  When 2.5 wt\% water is added, R-double disappears, but the helical reflections characteristic
-%  of the parallel displaced configuration become more diffuse, which is a closer match to 
-%  experiment. If water is truly responsible for R-double, then there is likely
-%  between 1 and 2.5 wt\% water absorbed into the membrane. 
-%%MRS7: this is limited by the force field and strength of hydrogen bonding. ``is likely'' is strong.
-%This does not exclude 
-%  possible contributions from the motifs discussed in section~\ref{section:rdouble}. Water
-%  may facilitate the stability of such motifs. 
-%%  However, given the long-term stability of this configuration, it is most likely that small
-%%  amounts of water are responsible for the existence of R-double.  
-%  
-%%MRS7: should this be first in the section as motivation.
-%  The systems studied by Feng et al.\cite{feng_scalable_2014,feng_thin_2016} were not truly
-%  thermotropic Col\textsubscript{h} phases. Rather, they were very low water content 
-%  H\textsubscript{II} phases unintentionally created due to the neat monomers' hydroscopicity.
-%  This detail may be important for reproducing the results of Feng et al.
-%  
-%  R-double appears due to the structure of the head groups. We removed the head groups from the
-%  trajectory used to produce Figure~\ref{fig:solvation}a in order to produce that shown
-%  in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear without the influence of the
-%  head groups. Water molecules must play a role in the structuring of the head groups since 
-%  R-double does not appear in any dry simulations.
-%  
-%%  Water causes the monomer head groups to restructure.   
-%%  We confirmed that the reflection is 
-%%  not caused by the water itself. We removed all water molecules from the trajectory and 
-%%  showed that R-double is still present in the simulated diffraction pattern 
-%%  (Figure~\ref{fig:rdouble_nowater}). We also confirmed that the tails are not responsible for
-%%  R-double. R-double is not present when we remove all atoms except carbon atoms that make
-%%  up the tails (Figure~\ref{fig:rdouble_tails}). It is clear that interactions between water
-%%  and head groups causes them to restructure in a way that leads to R-double.
-%  
-%  
-%  % BJC5: This figure may belong in supplemental
-%  \begin{figure}[!htb]
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
-%  \caption{Full system}\label{fig:rdouble_offset}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
-%  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
-%  \end{subfigure}
-%%  \begin{subfigure}{0.32\textwidth}
-%%  \includegraphics[width=\textwidth]{rdouble_tails_only_rzplot.png}
-%%  \caption{Tails only}\label{fig:rdouble_tails}
-%%  \end{subfigure}
-%  \caption{The structure of the head groups is responsible for the appearance of
-%  R-double in (a). Removing head groups from the trajectory results in a simulated 
-%  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
-%  \end{figure}
-%
-%  When two vertically stacked monomer head groups hydrogen bond with a shared water 
-%  molecule, the monomers are drawn closer together (as illustrated in 
-%  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows 
-%  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
-%  with a head group below itself, it will be less likely to share a water molecule 
-%  with a head group above it due to steric constraints. The monomer head group above
-%  can just as easily share a water molecule with a head group above itself. In this scenario,
-%  the centers of each group are 2 times the $\pi$-stacking distance apart which would
-%  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
-%  a modest number of occurrences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
-%  Peaks in the distributions represent the scenario where a monomer head group shares a 
-%  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
-%  we calculated the discrete Fourier transform of the distributions which we used as a rough 
-%  indicator of whether the head group arrangement will lead to R-double. We see the 
-%  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
-%  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.
-%
-%%MRS7: probably want to say that this is a likely mechanism, if it can
-%%occur with the given forcefield, since we had a hard time identifying any others. A more realistic forcefield
-%% may make the effect stronger.
-%  
-%  \begin{figure}[!htb]
-%  \centering
-%  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
-%  % to the floating head groups)
-%  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
-%  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
-%  drawn closer together. Head groups with blue bonds were stacked above those 
-%  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
-%  \end{figure}
-%  
-%  \begin{figure}[!htb]
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{pore_hbonds.png}
-%  \caption{}\label{fig:pore_hbonds}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
-%  \caption{}\label{fig:pore_hbonds_ft}
-%  \end{subfigure}
-%  %MRS7: add a bit more explanation - no description of discrete FT.
-%  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
-%  shared hydrogen bonded water molecule between a monomer head group and that stacked
-%  vertically above it. (b) }\label{fig:hbond_quantification}
-%  \end{figure}
-
-%  The appearance of R-double may be due to increased order of the pores. The first
-%  peak of the correlation function, $g(z)$, is approximately 30\% larger in the 
-%  solvated versus dry configuration (Figure~\ref{fig:solvated_correlation_overlay}).
-%  Based on the peak locations, it is evident that the head groups stack closer 
-%  together in the solvated configuration which may play a role in enforcing order.
-%  This may be in part due to swelling of the pores. In 
-%  Figure~\ref{fig:head_group_density_overlay} there is a clear decrease in 
-%  head group density within 0.4 nm of the pore center. Water molecules may swell 
-%  the pores and hydrogen bond with monomer head groups, tethering the monomers 
-%  closer together. If this is the case, then it implies that R-double has always
-%  been at least weakly present in the simulated diffraction patterns, but may 
-%  have been buried by noise.
-% 
-%  \begin{figure}[!htb]
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{solvated_correlation_overlay.png}
-%  \caption{}\label{fig:solvated_correlation_overlay}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{head_group_density_overlay.png}
-%  \caption{}\label{fig:head_group_density_overlay}
-%  \end{subfigure}
-%  \caption{}\label{fig:rdouble_structuring}
-%  \end{figure}
-
-%  In all cases, water disrupts structuring of the model. When we add water to
-%  the system, the intensity of the reflections decrease. In systems built with 5
-%  wt\% water, R-$\pi$ and R-spots become nearly indistinguishable from R-alkanes.
-%  In systems built with 5 wt\% water, the pore region becomes filled with
-%  water. We plotted the number density of components in this system. As with the 
-%  dry systems, we see a gradual compositional transition from hydrophilic to hydrophobic.  
-%  We see that the pores become a mixture of water molecules and sodium ions (Fig.
-%  \ref{fig:water_density}). We also see that water exists in the tail region which 
-%  may decrease the tail ordering and explain the decrease in intensity of R-spots.
-%  
-%  The membrane swells when we introduce water. The location of maximum head
-%  group density shifts from 0.35 to 0.62 nm and from 0.44 to 0.61 nm in the
-%  parallel displaced and sandwiched configurations respectively. Again, we
-%  observe the existence of ions, head groups and water outside the pore region,
-%  however in the hydrated system, the head groups drift beyond 1.5 nm from the
-%  pore center. In the dry systems, head groups did not wander beyond 1.4 nm from
-%  the pore center. Both observations suggest that water pushes all components
-%  radially outward from the pore center, characteristic of a swelling process.
-%  The plots of $g(x,y)$ for dry and wet systems are compared in
-%  Figure~\ref{fig:solvated_correlation}. They further illustrate how the system
-%  swells in the presence of water. This system is a closer representation
-%  of the H\textsubscript{II} phase which is typically synthesized with ca. 8 wt\%
-%  water. Further investigation of hydrated systems can help unravel the
-%  mechanisms for selective transport in separations of aqueous solutions. 
-%
-%  Water is not necessary to maintain an ordered pore structure. We do not
-%  eliminate the possibility that water is necessary in order to drive
-%  self-assembly, but studying the mechanisms of self-assembly is beyond the
-%  scope of this work. According to our model, once the system has formed the
-%  Col\textsubscript{h} phase, adding water only drives disorder of the pore
-%  structure. In the true equilibrium configuration, if water exists, it is
-%  primarily confined to the pore region where there is no driving force for
-%  aggregation of water molecules. In the case of trace water, water molecules
-%  will be too sparse to form a hydrogen bonding network.
-%
-%  \begin{figure}
-%  \centering 
-%  \begin{subfigure}{0.45\textwidth}
-%        \includegraphics[width=1\linewidth]{offset_solvated_density.png}
-%        \caption{Parallel Displaced}
-%        \label{fig:offset_solvated_density}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%        \includegraphics[width=1\linewidth]{layered_solvated_density.png}
-%        \caption{Sandwiched}
-%        \label{fig:layered_solvated_density}
-%  \end{subfigure}
-%  \caption{Water fills the membrane pores in the parallel displaced (a) and
-%	  sandwiched (b) configurations. Head groups in the sandwiched configuration sit
-%	  closer to the pore center than they do in the parallel displaced configuration.
-%	  Both systems are composed primarily of water close to the pore center.}
-%  \label{fig:water_density}
-%  \end{figure}
-%
-%  %BJC: this may be okay to push to supplemental
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.47\textwidth}
-%        \includegraphics[width=1\linewidth]{layered_xy_correlation.png}
-%        \caption{Sandwiched, Dry}
-%        \label{fig:layered_xy_correlation_comparison}
-%  \end{subfigure}
-%  \begin{subfigure}{0.47\textwidth}
-%        \includegraphics[width=1\linewidth]{layered_solvated_xy_correlation.png}
-%        \caption{Sandwiched, Solvated}
-%        \label{fig:layered_solvated_xy_correlation}
-%  \end{subfigure}
-%  \begin{subfigure}{0.47\textwidth}
-%        \includegraphics[width=1\linewidth]{offset_xy_correlation.png}
-%        \caption{Parallel Displaced, Dry}
-%        \label{fig:offset_xy_correlation_comparison}
-%  \end{subfigure}
-%  \begin{subfigure}{0.47\textwidth}
-%        \includegraphics[width=1\linewidth]{offset_solvated_xy_correlation.png}
-%        \caption{Sandwiched, Solvated}
-%        \label{fig:offset_solvated_xy_correlation}
-%  \end{subfigure}
-%  \caption{$g(x,y)$ of monomer head groups illustrates how the pores
-%	  swell in the presence of water.}~\label{fig:solvated_correlation}
-%  \end{figure}
 
@@
 
-%  Our systems may be frozen in a glassy state. It is also possible that we are simply 
-%  observing characteristics of the experimental system. There has been no experimental work
-%  done to study diffusion of Na-GA3C11 monomers in the Col\textsubscript{h}
-%  system and no measurement of the glass transition temperature. Such a low
-%  diffusion constant is not unheard of. A more recent study reported a diffusion
-%  constant of $1.2\times10^{-14}~m^2/s$ for a different liquid crystal that
-%  formed a hexagonal columnar phase \cite{dvinskikh_molecular_2002}.
-
-%MRS6: I don't know that the equilibration procedure induces it; I doubt a metastable state would have slower kinetics than the real state. It might be the force field is too stable. 
-%  It is possible that our equilibration procedure may induce glassy phase
-%  configurations. We have already shown that our system has some dependence on
-%  initial configuration. It is conceivable that after a fast initial relaxation,
-%  the system gets locked into a structure close to its initial configuration.
-%  The glassy state of these systems may be the reason we observe such high
-%  correlation lengths in the ordered pore basin systems. Unfortunately, we are
-%  unable to resolve the exact atomistic structure using existing experimental
-%  techniques, so we are left to find out which initial configuration results in a
-%  model with the closest match to experimental data.
-
   Consequently, there is not enough movement on the timescales we simulated for the system to 
-  consistently reach a definitive equilibrium structure.
-  %MRS13:removed phrase, since long time scale does not guarantee closer to experiment. 
-  %equivalent to experiment. 
-  In all cases our monomers
+  consistently reach a definitive equilibrium structure. In all cases our monomers
   equilibrate to a stacking distance that is too large compared to experiment. 
-  As discussed in section~\ref{section:rpi},
-  while this may be in large part due to the force field's inability to model aromatic
-  interactions, it is also possible that the monomer tails do have enough time to pack 
-  as tightly as they could. More densely packed tails could allow the monomers to stack
-  closer together.
+  As discussed in section~\ref{section:rpi}, while this may be in large part due to the 
+  force field's inability to model aromatic interactions, it is also possible that the
+  monomer tails do have enough time to pack as tightly as they could. More densely packed
+  tails could allow the monomers to stack closer together.
 
@@
   the scope of the current study.
-  % 800K simulations are worse. Over 400 ns, the z box dimension goes to 9.8. I think this
-  % is because the initial box z-box dimension is ~10.9. In the 500K system, the initial
-  % z-box dimension is ~9.7
-
-%MRS5: let's talk about the implications of this (above); might want to move some of this into the SI.
-%BJC6: Which could be moved to supplemental? Theoretically, I could move most of the dihedral
-% stuff to SI and summarize briefly. But it I think it makes what we did more abstract.
-%MRS8: I think that you can just give the numbers  in the text, and move the figures to SI? Figures don't add a lot.
 
@@
   \subsection{Ionic Conductivity Measurements}
-
-  %BJC5: which system should I study here? I wrote this before the solvated
-  % system showed R-double. It might make sense to study the solvated system for ionic
-  % conductivity and cross-linking.
-
-  %MRS7: hmm.
-Good question.
-Probably, as long as it's pretty straightforward.
-For diffusion, you can do just one calculation, and put the alternate method in SI (you can mention you did it, i.e.
-we did X, it was noisier, but agreed within data (see SI).
-
-  %BJC6: shifted to solvated system only. Moved Collective diffusion to supporting info.
-
-%  We used equilibrated systems in the ordered pore basin to calculate ionic 
-%  conductivity since we believe their structures are the closest match to
-%  experiment.
 
@@
   simulations to lower.
-
-%  We compare calculated values of ionic conductivity obtained using the 
-%  Nernst-Einstein relation and Collective Diffusion model in Figure~\ref{fig:conductivity}.
-%  The two methods agree with each other within error, although the uncertainty
-%  obtained using the Collective Diffusion model is much higher. We require much longer simulations to lower the uncertainty,
-%  however it is not feasible to do so with a large system. We will only use the
-%  Nernst-Einstein relation in future calculations of this type.
-
-% BJC15: removed figure
-%  \begin{figure}
-%  \centering
-%  \includegraphics[width=0.5\textwidth]{IC_nernst.png}
-%  \caption{The calculated ionic conductivity of the simulated system is approximately
-%  one order of magnitude higher than experiment.}\label{fig:ionic_conductivity}
-%  \end{figure}
 
@@
 
-  % BJC5: Is it worth including the distance between layers and the correlation length? 
-  % MRS8: probably very briefly discuss the changes, to justify the use of the word ``minor''
   There are only minor changes to the physical characteristics of these systems when 
@@
   \end{figure}
-  %MRS13: would be good to have labels on the upper bar chart x-axis as well. 
-%  The system's structure and physical characteristics did not change
-%  significantly when we applied the cross-linking algorithm to the equilibrated
-%  parallel-displaced configuration in the ordered pore basin. We simulated
-%  the cross-linked system in the NPT ensemble for 100 ns. After the system is
-%  cross-linked, the distance between pores shrinks by 0.4 \AA~and the distance
-%  between layers increases by 0.04 \AA. All major features are still present in
-%  the simulated XRD patterns, however at lower intensities
-%  (Fig.~\ref{fig:rzplot_xlink}). We calculated the ionic conductivity using the
-%  Nernst-Einstein relation and found that it is lower in the cross-linked system
-%  (Fig.~\ref{fig:IC_xlink}).
-
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%	\centering
-%	\includegraphics[width=\textwidth]{rzplot_xlink.png}
-%	\caption{}~\label{fig:rzplot_xlink}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%	\centering
-%	\includegraphics[width=\textwidth]{IC_xlink.png}
-%	\caption{}~\label{fig:IC_xlink}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%	\centering
-%	\includegraphics[width=\textwidth]{dbwl_xlink.png}
-%	\caption{}~\label{fig:dbwl_xlink}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%	\centering
-%	\includegraphics[width=\textwidth]{p2p_xlink.png}
-%	\caption{}~\label{fig:p2p_xlink}
-%  \end{subfigure}
-%  \caption{Applying our simulated crosslinking mechanism to an equilibrium
-%	  configuration causes slight changes to the system's physical and structural
-%	  properties. (a) Reflections produced by the cross-linked configuration are
-%	  faded relative to the uncross-linked system. (b) The ionic conductivity is
-%	  smaller relative to the uncross-linked system, but still much larger than the
-%	  experimental value. When the system is cross-linked, the distance between
-%	  layers increases (c) and the pore spacing decreases (d)}~\label{fig:xlink}
-%  \end{figure}
 
@@
 
-%MRS6: I think we should remove the ``we learned'', and express it more in terms of the observed facts: rather than ``we learned statement X'', you can just say ``statement X''.
-Or ``observation Y in the simulations supports the conclusion Y''.
   We have used detailed molecular modeling of the Col\textsubscript{h} phase
@@
 
-%  The system's pore spacing is most consistent with experiment when systems
-%  are built with 5 columns per pore. The distance between pores increases with the 
-%  number of columns per pore. Pores pack closer together in the disordered pore 
-%  basin. Systems built with 6 columns per pore in the disordered basin expand in 
-%  the z-direction which suggest that it may rearrange to 5 columns per pore long term.
-
-%  We have maximized our model's consistency with the experimental WAXS pattern. We show
-%  that R-alkanes and R-pores appear where expected. We learned that R-spots is likely 
-%  due to ordered alkane chain packing. R-$\pi$ appears at lower q values than experiment
-%  because monomer stack too far apart. We learned that our model reproduces R-double when
-%  we add 1 wt\% water to the system.
-
   We characterized the environment centered around the membrane pores and
@@
   Finally, we verified that our conclusions do not change when the system is
-  cross-linked by the algorithm we implemented. The diffraction pattern weakens
-  relative to the uncross-linked system, 
-  %MRS13: I might have missed you mentioning this point before? Make sure it is in the results text.
-  ionic conductivity drops by a factor
+  cross-linked by the algorithm we implemented. The ionic conductivity drops by a factor
   of $\sim$1.5, in closer agreement with experiment, the pore spacing decreases and
@@
   preserving most of the features well.
-
-%MRS6'' isn't it 1-3 orders of magnitude lower?
-You cite some slower statistics, and there might be differences between lyotropic and thermotropic, if the hydrophilic/hydrophobic effect is stronger than the effects in thermotropic fluids.
-%  We acknowledge that our simulated system exhibits glassy dynamics. The
-%  measured diffusion constants of monomers are one to three orders of magnitude lower
-%  than expected. It is possible that our equilibration procedure induces these
-%  types of metastable phases. It is also possible that the observed dynamics are
-%  characteristic of the real system. We took great care to overcome the potential
-%  limitations of our equilibration procedure and have come up with a structure
-%  that is in good agreement with experimental data.
 
@@
   \newpage
-  %BJC: TOC graphic
 

### 2018-10-08 Ben_Manuscripts/structure_paper/Final_Draft.tex
new comments
Responded to comments. Made axis labels bigger on plots.

@@
         \end{subfigure}
-	\begin{subfigure}[t]{0.405\linewidth}
+	\begin{subfigure}[t]{0.38\linewidth}
                 \centering
@@
 
+  \subsection{Source code}
+
+  Python scripts used to conduct post-simulation trajectory analysis, are available online at \\ 
+  \texttt{https://github.com/bencoscia/llcsim}. The python scripts used to simulated XRD
+  patterns are publicly available online at \texttt{https://github.com/joeyelk/MD-Structure-Factor}. 
+  Additional details are available in Section \ref{S-section:python_scripts} of the SI.
+
   \subsection{Monomer Parameterization}
@@
   configuration from the trajectory which we used for full system
-  construction (Figure~\ref{fig:build_procedure}a). Section S-\ref{S-section:parameterization} 
-  of the Supporting Information provides further detail of the parameterization process.
+  construction. Section \ref{S-section:parameterization} 
+  of the Supporting Information (SI) provides further detail of the parameterization process.
 
@@
   \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system (see Section S-\ref{S-section:self_assembly} of the 
-  Supporting Information). 
-  To bypass the slow self-assembly process, we used a variety of automated procedures 
-  to assemble monomers into a structure close to one of a number of hypothesized equilibrium configurations
-  (Figure~\ref{fig:build_procedure}).
-  %MRSF: where's the reference for the build scripts repository?
-  %MRS13: Would be nice to say we put the scripts on GitHub.  Additional details about which scripts can be in supporting.
-  These initial structures may result in equilibration into slowly-intercoverting
-  metastable states, an issue we will address later in the paper.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}[t]{0.45\textwidth}
-  \includegraphics[width=\linewidth]{monomer_diagonal.pdf}
-  \caption{}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.42\textwidth}
-  \includegraphics[width=\linewidth]{stacked_monomers.pdf}
-  \caption{}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.35\textwidth}
-  \includegraphics[width=\linewidth]{initial_pore.pdf}
-  \caption{}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.45\textwidth}
-  \includegraphics[width=\linewidth]{initial_unit_cell.pdf}
-  \caption{}
-  \end{subfigure}
-  %MRSF: I think this can be put in Supporting Information (we will get pushback to make this paper shorter, this is a good candidate)
-  \caption{(a) We parameterized a single monomer and annealed it to produce a low-energy
-		configuration. (b) We assembled monomers into columns by stacking them on top of each 
-		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
-		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
-		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{fig:build_procedure}
-  \end{figure}
+  indicators of progress towards an ordered system (see Section \ref{S-section:self_assembly} of the 
+  SI). To bypass the slow self-assembly process, we used a 
+  variety of automated procedures to assemble monomers into a structure close to
+  one of a number of hypothesized equilibrium configurations (See Figure 
+  \ref{S-fig:build_procedure} of the SI). These initial structures may result
+  in equilibration into slowly-intercoverting metastable states, an issue we will
+  address later in the paper.
 
@@
   and to obtain sufficient resolution when simulating XRD patterns (see further discussion
-  in Section S-\ref{S-section:monomers_per_column} of the Supporting Information).
+  in Section \ref{S-section:monomers_per_column} of the SI).
 
@@
   experimental value of 4.12 nm for our initial configurations. A sensitivity analysis of 
-  both parameters is presented in the Supporting Information, Section S-\ref{S-section:initial_config_dependence}. The 
+  both parameters is presented in the SI, Section \ref{S-section:initial_config_dependence}. The 
   distance between vertically stacked monomers, the xy position of monomers with respect 
@@
   \AA. However this largest spacing yields non-physical behavior which is detailed in the 
-  Supporting Information, Section S-\ref{S-section:initial_dbwl}.
+  SI, Section \ref{S-section:initial_dbwl}.
 
@@
   of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See Figure 
-  S-\ref{S-fig:stacking} of the Supporting Information for a detailed illustration 
+  \ref{S-fig:stacking} of the SI for a detailed illustration 
   of the initial configurations in each mode.
@@
   least 400 ns using the Parrinello-Rahman barostat. More equilibration details
-  are given in Section S-\ref{S-section:equilibration} of the Supporting Information.
+  are given in Section \ref{S-section:equilibration} of the SI.
 
@@
   ions in their respective pores. We generated pore spacing statistics 
-  using the bootstrapping technique (See Section S-\ref{S-section:p2p_stats} of the
-  Supporting Information). 
+  using the bootstrapping technique (See Section \ref{S-section:p2p_stats} of the
+  SI). 
   The pore spacings calculated in this way are consistent
-  with one half of the $x$ and $y$ box vectors (See, Table S-\ref{S-table:p2p} in the
-  Supporting Information). However, our method for their calculation does a better 
+  with one half of the $x$ and $y$ box vectors (See, Table \ref{S-table:p2p} in the
+  SI). However, our method for their calculation does a better 
   job capturing the spread of pore-to-pore distances.
@@
   we used the $q_r$ cross-section of 2D-SAXS which was generated from the same
-  sample (Figure S-\ref{S-fig:2DSAXS} of the Supporting Information). Since the d\textsubscript{200} peak is
+  sample (Figure \ref{S-fig:2DSAXS} of the SI). Since the d\textsubscript{200} peak is
   partially exposed in the experimental 2D-WAXS pattern, we normalized the
@@
   atoms in each group from the pore centers, then normalized by the volume of the
-  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}
-  of the Supporting Information).
+  annulus defined by the bin edges and the z box vector (See Figure \ref{S-fig:rdf_diagram}
+  of the SI).
 
@@
   measured ion concentration with respect to the volume of the entire unit cell. 
-  More details are provided in the Supporting Information, Section~S-\ref{S-section:ionic_conductivity}.
+  More details are provided in the SI, Section \ref{S-section:ionic_conductivity}.
 
@@
   We based our cross-linking algorithm on the known reaction mechanism 
-  (Figure S-\ref{S-fig:xlink_mech} of the Supporting Information). The reaction 
+  (Figure \ref{S-fig:xlink_mech} of the SI). The reaction 
   takes place at the terminal vinyl groups
@@
   the next group of eligible carbons atoms.
-
-  \subsection{Source code}
-  %MRSF: Suggest moving these references to where each code is described instead of separately here.
-  %BJC: the hyperref package really messes up the labels
-  The python scripts used to simulated XRD patterns are publicly available online at \\
-  \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Python scripts used to conduct
-  all other post-simulation trajectory analysis, are also available online at \\ 
-  \texttt{https://github.com/bencoscia/llcsim}.
-  %BJC: llcsim repository only contains necessary scripts. Should probably move to Shirts-group repo
 
@@
   spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional 
-  systems with monomers initially spaced 5 \AA~apart vertically (see Section~\ref{S-section:initial_pore_spacing}
-  of the Supporting Information for more details on sensitivity to initial monomer spacing). 
+  systems with monomers initially spaced 5 \AA~apart vertically (see Section \ref{S-section:initial_pore_spacing}
+  of the SI for more details on sensitivity to initial monomer spacing). 
   We considered the pore-to-pore spacing to be equilibrated as defined in Section~\ref{method:equil_time}.
@@
   quantified the ordering of the head groups using the nematic order parameter (see Section 
-  S-\ref{S-method:nematic_order} for details of the calculation). Disordered basin systems have
+  \ref{S-method:nematic_order} for details of the calculation). Disordered basin systems have
   a lower nematic order parameter (meaning they are more disordered) than ordered basin systems. 
@@
   with experimental stacking distances derived from WAXS relative to ordered basin systems 
-  (See section~\ref{section:rpi}).
+  (See Section~\ref{section:rpi}).
 
@@
   with the most unambiguous XRD features, the pore-to-pore spacing
-  and the stacking distance, as described in section~\ref{section:mon_per_pore}. 
+  and the stacking distance, as described in Section~\ref{section:mon_per_pore}. 
   We generated simulated patterns using the locally
@@
   independent configurations within their respective metastable basins (see
-  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting
+  Section~\ref{section:slow_dynamics}), meaning we must take care in interpreting
   the results of the XRD. The amount of independent configurations required to 
-  converge along the $q_z$ axis is analyzed in Supporting Information, 
-  Section S-\ref{S-section:xrd_noise}. The simulated patterns generated for all
+  converge along the $q_z$ axis is analyzed in SI, 
+  Section \ref{S-section:xrd_noise}. The simulated patterns generated for all
   systems studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
@@
 	\centering
-	\begin{subfigure}{0.88\textwidth}
+	\begin{subfigure}{0.905\textwidth}
 	\begin{subfigure}{0.28\linewidth}
@@
 	\end{subfigure}
-	\begin{subfigure}{0.1\textwidth}
+	\begin{subfigure}{0.085\textwidth}
 		\centering
@@
   \begin{itemize}
-  	\item The location of R-alkanes (section~\ref{section:ralkanes})
-  	\item The location and intensity of R-pores (section~\ref{section:rpores})
+  	\item The location of R-alkanes (Section~\ref{section:ralkanes})
+  	\item The location and intensity of R-pores (Section~\ref{section:rpores})
   \end{itemize}
@@
   tilt relative to the $xy$ plane to an angle statisically indistinguishable from
-  zero (see Section~S-\ref{S-section:tail_tilt} of the Supporting Information).
+  zero (see Section \ref{S-section:tail_tilt} of the SI).
 
@@
   off at the tail ends, where there is more space to fill causing them
-  to pack nearly isotropically. See Section~S-\ref{S-section:tail_packing} 
-  of the Supporting Information for
+  to pack nearly isotropically. See Section \ref{S-section:tail_packing} 
+  of the SI for
   a more detailed explanation of the calculation and packing
@@
   throughout $g(z)$ in both cases (See
-  Figure~S-\ref{S-fig:z_correlation_overlay}).
+  Figure \ref{S-fig:z_correlation_overlay}).
 
@@
   right amount of disorder on the $xy$ plane. However, the relatively low quality
-  of the fit implies that the FWHM may actually be different from experiment, and
-  %MRSF: what does optimization mean here? Better forcefield or longer time? Better fitting?
-  that the radial ordering of the head groups may benefit from further optimization.
+  of the fit implies that the FWHM of a fixed Lorentzian fit to data from a 
+  single simulation might not be the best comparison to experiment and that 
+  some form of initial configuration dependence causes extra structure.
+  %BJCF: new ending to this paragraph (above) 
+  %may actually be different from experiment, and
+  %that the radial ordering of the head groups may benefit from further optimization.
 
@@
 
+  %BJCF: broke giant paragraph into 3 paragraphs, adjusted theses
   Since the dynamics of this system are slow, and consequently most of our analysis
@@
   Equivalent data for the sandwiched configuration is presented in Section 
-  S\ref{S-section:sandwiched_ensemble}.
+  \ref{S-section:sandwiched_ensemble}.
 
@@
 I think also this paragraph should be split up more to emphasize findings.
+  %BJCF: thesis changed, added reminder of initial randomization.
   These short independent simulations exhibit a symmetric distribution of quenched
-  disorder. We pooled the deviations of each head group COM from idealized positions
-  from all independent simulations in order to create the distributions shown in 
-  Figure~\ref{fig:offset_ensemble_pooled} (see Section~\ref{method:simple_systems}).
+  disorder providing evidence that the quenched disorder is randomized in each system. 
+  We remind the reader that the only difference between each independent initial configuration
+  is the random $z$-direction displacement that we apply to each column. The
+  quenched disorder is then a result of the initial structural collapse that is 
+  directed by the randomized velocity vectors of the system's atoms which are drawn from
+  a Maxwell-Boltzmann distribution. We pooled the deviations of each head group COM 
+  from idealized positions from all independent simulations in order to create the 
+  distributions shown in Figure~\ref{fig:offset_ensemble_pooled} (see Section~\ref{method:simple_systems}).
   The distributions appear symmetric meaning that there is an equal chance for a head
@@
 
-  We verified that this same symmetry exists when looking at individual COMs.
+  %BJCF: broke into separate paragraph
+  We verified that this same symmetry exists for individual COMs.
   If we consider the COM of a given head group, we expect that the distribution of
@@
   the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
-  (see Figure~S-\ref{S-fig:between_pd} of the Supporting Information). In this way,
+  (see Figure \ref{S-fig:between_pd} of the SI). In this way,
   columns can more easily act 
@@
   since the group extends the system's $\pi$ conjugation~\cite{carey_organic_2011} (see Figure
-  S-\ref{S-fig:carboxylate_dihedral_rb} of the Supporting Information), which is significant even considering
+  \ref{S-fig:carboxylate_dihedral_rb} of the SI), which is significant even considering
   possible overestimates of the barrier height in the classical force field.
@@
   Simulated XRD patterns of all other solvated systems tested are shown in Figure
-  S-\ref{S-fig:solvation}, however R-double is not present.
+  \ref{S-fig:solvation}, however R-double is not present.
 
@@
   modest number of occurrences of this scenario, which we quantify in further
-  detail in the Supporting Information, Section S-\ref{S-section:rdouble}.
+  detail in the SI, Section \ref{S-section:rdouble}.
 
@@
   region, we used heavy atoms making up the aromatic rings and carboxylate groups. For the tail
-  region, we used carbon atoms of the monomer tails (See Figure S-\ref{S-fig:monomer_color_coded}
-  of the Supporting Information for a diagram). We averaged the histograms over the equilibrated
+  region, we used carbon atoms of the monomer tails (See Figure \ref{S-fig:monomer_color_coded}
+  of the SI for a diagram). We averaged the histograms over the equilibrated
   portion of the trajectory. 
@@
 
-  % BJC6: edited to reduce comparison to other columnar LCs (and shortened)
   We observe slow dynamics in our system. Typical diffusion constants for columnar
@@
   %energies involved.
-  %MRS13: are these hydrophulic/hydrophopic LC?  Once with electrostatic driving forces are likely 
+  %MRS13: are these hydrophilic/hydrophopic LC?  Ones with electrostatic driving forces are likely 
   % to be even slower.  
-  We measured the diffusion constants of monomers in each of the systems we
-  studied (see Table S-\ref{S-table:msd} of the Supporting Information) and find they are all on the order of
-  $10^{-14}~\mathrm{m}^2/\mathrm{s}$. However, since on this timescale, no monomers move
-  a full `level' above or below, this may be an overestimate. This slow speed is
-  not entirely surprising considering how densely the monomers are
-  packed as implied by diffraction experiments. The entangled tails
-  likely restrict both vertical and lateral movement.
+  %BJCF: new addtion
+  In the case of LLCs, we would expect a diffusion coefficient at the low end of this
+  range since hydrophilic regions of monomers can hydrogen bond, thus increasing the energy 
+  barrier for motion. We measured the diffusion constants of monomers in each of the main 
+  systems we studied (see Table \ref{S-table:msd} of the SI) and find they are all on the 
+  order of $10^{-14}~\mathrm{m}^2/\mathrm{s}$. However, since on this timescale, no monomers 
+  move a full `level' above or below, this may be an overestimate. This slow speed is
+  not entirely surprising considering how densely the monomers are packed as implied
+  by diffraction experiments. The entangled tails likely restrict both vertical and lateral
+  movement.
 
@@
   equilibrate to a stacking distance that is too large compared to experiment. 
-  As discussed in section~\ref{section:rpi}, while this may be in large part due to the 
+  As discussed in Section~\ref{section:rpi}, while this may be in large part due to the 
   force field's inability to model aromatic interactions, it is also possible that the
@@
   head groups and the ether oxygens which attach the tails to the head group 
-  (see Figure S-\ref{S-fig:dihedrals} of the Supporting Information). We exclude the dihedral from the middle tail 
+  (see Figure \ref{S-fig:dihedrals} of the SI). We exclude the dihedral from the middle tail 
   since it is fundamentally different than the two symmetric outside tails. We 
@@
   relationship using the collective diffusion model\cite{liu_collective_2013} 
-  (see section S-\ref{S-fig:conductivity} of the Supporting Information). The values calculated by the 
+  (see Section \ref{S-fig:conductivity} of the SI). The values calculated by the 
   collective diffusion model agree with Nernst-Einstein values within error, 
@@
   monomers were either involved in a cross-linking reaction or were terminated 
-  (see Section S-\ref{S-section:xlink} of the Supporting Information)
+  (see Section \ref{S-section:xlink} of the SI)
   for further details of the cross-linking algorithm). We allowed the cross-linked

### 2018-10-08 Ben_Manuscripts/structure_paper/supporting_information.tex
Responded to comments. Made axis labels bigger on plots.

@@
 
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thesection}{S\arabic{section}}
+
 %\SectionNumbersOn
@@
   \maketitle
+
+  \section{Analysis scripts}\label{section:python_scripts}
 
@@
   maintains its isotropic alignment.}\label{fig:self_assembly}
+  \end{figure}
+
+  \section{Monomer build procedure}\label{section:monomer_build_procedure}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}[t]{0.45\textwidth}
+  \includegraphics[width=\linewidth]{monomer_diagonal.pdf}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.42\textwidth}
+  \includegraphics[width=\linewidth]{stacked_monomers.pdf}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.35\textwidth}
+  \includegraphics[width=\linewidth]{initial_pore.pdf}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.45\textwidth}
+  \includegraphics[width=\linewidth]{initial_unit_cell.pdf}
+  \caption{}
+  \end{subfigure}
+  %MRSF: I think this can be put in Supporting Information (we will get pushback to make this paper shorter, this is a good candidate)
+  \caption{(a) We parameterized a single monomer and annealed it to produce a low-energy
+		configuration. (b) We assembled monomers into columns by stacking them on top of each 
+		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
+		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
+		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{fig:build_procedure}
   \end{figure}
@@
   Parallel Displaced, Disordered & $3.5 \times 10^{-14}$ \\
+  Parallel Displaced, 1 wt \% water & $7.1 \times 10^{-14}$ \\
   \bottomrule

### 2018-10-09 Ben_Manuscripts/structure_paper/Final_Draft.tex
Modified figures for paper
minor edits and formatting

@@
 
-  Python scripts used to conduct post-simulation trajectory analysis, are available online at \\ 
-  \texttt{https://github.com/bencoscia/llcsim}. The python scripts used to simulated XRD
-  patterns are publicly available online at \texttt{https://github.com/joeyelk/MD-Structure-Factor}. 
-  Additional details are available in Section \ref{S-section:python_scripts} of the SI.
-
-  \subsection{Monomer Parameterization}
+  Python scripts used to set up systems and conduct post-simulation trajectory analysis are
+  available online at \texttt{https://github.com/bencoscia/llcsim}. The python scripts used
+  to simulated XRD patterns are publicly available online at \\
+  \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Additional details are available in 
+  Section \ref{S-section:python_scripts} of the SI.
+
+  \subsection{Monomer Parameterization}\label{method:parameterization}
 
@@
 
-  \subsection{Unit Cell Preparation}
+  \subsection{Unit Cell Preparation}\label{method:unitcell_build}
 
@@
 
-  \subsection{Monomer Placement}
+  \subsection{Monomer Placement}\label{method:monomer_placement}
 
@@
 
-  \subsubsection{\textit{Radial distribution functions}}
+  \subsubsection{\textit{Radial distribution functions}}\label{method:rdfs}
 
@@
 
-  \subsection{\textit{Ionic conductivity calculations}}
+  \subsection{\textit{Ionic conductivity calculations}}\label{method:ionic_conductivity}
 
@@
 
-  \subsection{Cross-linking}
+  \subsection{Cross-linking}\label{method:xlink}
 
@@
   \centering
-  \begin{subfigure}{0.3\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{sf_qy_sr0.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.3\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{sf_qy_sr75.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.3\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{sf_qy_sr100.pdf}
@@
 %  \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
+  \begin{subfigure}{0.325\linewidth}
   	\centering
@@
   \end{subfigure}
-  \begin{subfigure}{0.3\linewidth}
+  \begin{subfigure}{0.325\linewidth}
   	\centering

### 2018-10-09 Ben_Manuscripts/structure_paper/supporting_information.tex
minor edits and formatting

@@
 \usepackage{xr}
+\usepackage{array}
+\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
 
@@
 
-\externaldocument[M-]{Draft}
+\externaldocument[M-]{Final_Draft}
 \title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
@@
 
-  \section{Analysis scripts}\label{section:python_scripts}
+  \section{Setup and analysis scripts}\label{section:python_scripts}
+
+  All python and bash scripts used to set up systems and conduct post-simulation trajectory
+  analysis, except for simulating X-ray diffraction (XRD) patterns, are available online at
+  \texttt{https://github.com/bencoscia/llcsim}. Table~\ref{table:python_scripts} provides more 
+  detail about specific scripts used for each type of analysis performed in the main text.
+
+  The python scripts used to simulated XRD patterns are publicly available online at \\
+  \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Given a GROMACS trajectory 
+  (.trr or .xtc) and a configuration file (.gro), simulate an XRD pattern using
+  \texttt{main\_gromacs.py}. Pass the flag \texttt{\-manuscript\_format} to generate patterns
+  and cross-sections with the same format as those presented in the main text.
 
@@
   \end{enumerate}
-  \clearpage
+
   \begin{figure}[!htb]
@@
   \end{figure}
+
+  \clearpage
+
+  \begin{table}[htb!]
+  \centering
+  \newcolumntype{A}{ >{\centering\arraybackslash} m{2.25in} }
+  \newcolumntype{B}{ >{\centering\arraybackslash} m{0.75in} }
+  \newcolumntype{C}{m{3in}}
+  \begin{tabular}{|A|B|C|}
+  \hline
+  \textbf{Script Name} & \textbf{Section} & ~~~~~~~~~~~~~~~~~~~~~\textbf{Description} \\
+  \hline
+  \texttt{/setup/param.sh} & \ref{M-method:parameterization} & Automatically run the monomer
+  parameterization scheme outlined in Section~\ref{section:parameterization} given an initial
+  structure file in .pdb format. \\ \hline
+
+  \texttt{/setup/build.py} & \ref{M-method:unitcell_build} \& \ref{M-method:monomer_placement} &
+  Build an initial configuration in the sandwiched or parallel displaced configuration with the 
+  desired initial vertical monomer spacing, monomers-per-column, and columns-per-pore. \\ \hline
+
+  \texttt{/setup/equil.sh} & \ref{M-section:equilibration} & Wrapper script for running the GROMACS 
+  functions and python scripts needed in order to equilibrate an initial configuration. \\ \hline
+
+  \texttt{/analysis/Structure\_char.py} & \ref{M-method:pore_spacing} & Calculate the distance 
+  between pores. \\ \hline
+
+  \texttt{/analysis/correlation.py} & \ref{M-section:correlation_length} & Calculate the 3D 
+  correlation function from a trajectory and plot desired slices. \\ \hline
+
+  \texttt{/analysis/regional\_density.py} & \ref{M-method:rdfs} & Calculate the density of a given
+  monomer component as a function of its distance from the pore center. \\ \hline
+
+  \texttt{/analysis/structure\_factor.py} & \ref{M-method:simple_systems} & Generate customizable
+  trajectories of point scatterers, then calculate their structure factor and plot slices of it.
+  \\ \hline
+
+  \texttt{/analysis/disorder.py} & \ref{M-method:simple_systems} & Measure the magnitude of
+  quenched disorder. \\ \hline
+
+  \texttt{/analysis/Ionic\_Conductivity.py} & \ref{M-method:ionic_conductivity} & Calculate the 
+  ionic conductivity using the Nernst-Einsten relationship and collective diffusion model. \\ \hline
+
+  \texttt{/setup/xlink.py} & \ref{M-method:xlink} & Iteratively cross-link a system given an 
+  initial configuration. \\ \hline
+
+  \texttt{/analysis/orientational\_order.py} & \ref{M-section:mon_per_pore} & Calculate the 
+  nematic order parameter. \\ \hline
+
+  \texttt{/analysis/tilt.py} & \ref{M-section:rspots} & Calculate the angle between the xy plane
+  and the vector extending from the front to the back of each monomer tail. \\ \hline
+
+  \texttt{/analysis/tail\_packing.py} & \ref{M-section:rspots} & Calculate the distribution of
+  angles between the center of mass of each monomer tail and its nearest neighbor monomer tails.
+  \\ \hline
+
+  \texttt{/analysis/compare\_disorder.py} & \ref{M-section:rpi} & Measure quenched disorder for
+  each trajectory in an ensemble of simulations, then plot distributions of quenched disorder.
+  \\ \hline
+
+  \texttt{/analysis/hbonds\_pairing.py} & \ref{M-section:rdouble} & Identify all hydrogen bonds
+  then count the number of monomer pairs that share hydrogen bonds. \\ \hline
+
+  \texttt{/analysis/torsions.py} & \ref{M-section:slow_dynamics} & Calculate the autocorrelation
+  function for a chosen dihedral. \\ \hline
+
+  \end{tabular}
+
+  \caption{The first column provides the names of the python scripts available in
+  the \texttt{llcsim} GitHub repository that were used for system setup and post-simulation 
+  trajectory analysis. Paths preceding script names are relative to the 
+  \texttt{llcsim} root directory. The second columns lists the section in the main
+  text where the output or usage of the script is first described. The third column
+  gives a brief description of the purpose of each script.
+  }~\label{table:python_scripts}
+
+  \end{table}
+
+  \clearpage
 
@@
 
+  \clearpage
+
   \section{Monomer build procedure}\label{section:monomer_build_procedure}
+
+  Figure~\ref{fig:build_procedure} illustrates the procedure carried out by 
+  \texttt{build.py} in order to build initial configurations.
 
@@
   equilibration follows the same procedure as the dry system.
+
+  \clearpage
 
@@
 
+  \clearpage
+
   \section{2D Small Angle X-ray Scattering Data}
@@
 
-  \section{Crosslinking algorithm details}\label{section:xlink}
+  \section{Cross-linking algorithm details}\label{section:xlink}
 
@@
 %  \end{figure}
+
+  \clearpage
 

### 2018-10-10 Ben_Manuscripts/structure_paper/Final_Draft.tex
Updated drafts.

@@
   highly correlated columns in our highly symmetric initial configurations.
+  %MRSF2: These next two sentences gets pretty confusing; too many clauses, if, when, since . . . make sentences shorter. 
   If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
@@
   %BJCF: broke giant paragraph into 3 paragraphs, adjusted theses
-  Since the dynamics of this system are slow, and consequently most of our analysis
+  %MRSF2: broke up the sentence, check to make sure it makes sense.
+  Since the dynamics of this system are slow, consequently most of our analysis
   has been focused on a set of quenched configurations with some structural 
-  characteristics that do not vary significantly with time, we attempted to learn
+  characteristics that do not vary significantly with time.  We therefore attempted to learn
   more about their time-averaged structures by studying ensembles of shorter 
-  simulations started from more independent initial configurations. We created
+  simulations started from more independent initial configurations. To do this, we created
   ensembles of 40 simulations in both the parallel displaced and sandwiched 
-  configurations. We used the same equilibration scheme as above 
-  (see Section~\ref{section:equilibration}). However, we built the initial 
+  configurations. We used the same equilibration scheme described in Section~\ref{section:equilibration}. 
+  However, we built the initial 
   configurations with columns randomly displaced in the $z$-direction and looked at
@@
   configurations. Compared to our long simulations, the intensity of R-$\pi$
-  generated from ensembles of short simulations, decreases by a factor of 3
+  generated from ensembles of short simulations decreases by a factor of 3
   and by a factor of 2 for the sandwiched and parallel displaced configurations respectively.
@@
   Overall, the intensity of R-$\pi$ generated from the parallel displaced 
-  ensemble shows the best agreement with experiment so far. For simplicity, 
+  ensemble of short simulations shows the best agreement with experiment so far. For simplicity, 
   we will limit the following discussion to the parallel displaced configuration.
-  Equivalent data for the sandwiched configuration is presented in Section 
+  Data for the sandwiched configuration is presented in Section 
   \ref{S-section:sandwiched_ensemble}.
@@
   disorder providing evidence that the quenched disorder is randomized in each system. 
-  We remind the reader that the only difference between each independent initial configuration
+  The only difference between each independent initial configuration
   is the random $z$-direction displacement that we apply to each column. The
   quenched disorder is then a result of the initial structural collapse that is 
-  directed by the randomized velocity vectors of the system's atoms which are drawn from
+  directed by the randomized velocity vectors of the system's atoms drawn from
   a Maxwell-Boltzmann distribution. We pooled the deviations of each head group COM 
@@
   In the case of LLCs, we would expect a diffusion coefficient at the low end of this
-  range since hydrophilic regions of monomers can hydrogen bond, thus increasing the energy 
-  barrier for motion. We measured the diffusion constants of monomers in each of the main 
+  range since hydrophilic regions of monomers can hydrogen bond, thus increasing the energetic 
+  barriers for motion. We measured the diffusion constants of monomers in each of the main 
   systems we studied (see Table \ref{S-table:msd} of the SI) and find they are all on the 

### 2018-10-10 Ben_Manuscripts/structure_paper/Final_Draft.tex
Follow-up edits

@@
   filtration processes that can be used to separate solutes on the order of 1 nm
-  in size and smaller, including 
-  %MRSF: this does seem to blend RO and NF together; is this correct, or are there important differences that should be outlined?
-  %BJCF: tried to differentiate them
-  ions. However, commercially available amorphous RO membranes and porous NF
-  membranes lack uniformity, which severely impacts their
-  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
+  in size and smaller, including ions. However, commercially available amorphous
+  RO membranes and porous NF membranes lack uniformity, which severely impacts
+  their selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
   fabrication involves the spontaneous assembly of polymers into disordered
-  structures that offer separation pathways that are tortuous and polydisperse
-  in size \cite{werber_materials_2016}. Tortuosity increases the effective
-  length that a solute must travel, while pore size polydispersity limits membrane
+  structures that offer separation pathways that are tortuous and polydisperse in
+  size \cite{werber_materials_2016}. Tortuosity increases the effective length
+  that a solute must travel, while pore size polydispersity limits membrane
   selectivity.
@@
 
-  Systems built with 5 columns around each pore equilibrate to a pore spacing that
-  is most consistent with the experimental value of 4.12 nm derived from SAXS
-  measurements (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4
+  Systems built with 5 columns around each pore equilibrate to a pore spacing
+  that is most consistent with the experimental value of 4.12 nm derived from
+  SAXS measurements (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4
   columns per pore equilibrate to an average pore spacing 0.25 nm lower than
@@
   disordered basin systems built with 6 columns-per-pore agree with experimental
-  pore-to-pore distances within error, but stack too far apart. 
-  %MRSF: not clear of the disordered ones below are for 5 or 6 columns
-  Monomers in 6 column-per-pore disordered sandwiched and disordered parallel displaced
+  pore-to-pore distances within error, but stack too far apart.  Monomers in 6
+  column-per-pore disordered sandwiched and disordered parallel displaced
   configurations stack $\sim$~4.87 and 4.94 \AA~apart respectively, which is
-  $\sim$ 1.2~\AA~further apart than suggested by experiment. 5 column-per-pore systems
-  stack, at a maximum, 0.9 \AA~further apart than experiment (see Table~\ref{table:correlation_length}).
-  The remainder of this discussion will therefore focus on the analysis of 
-  systems built with 5 columns per pore.
+  $\sim$ 1.2~\AA~further apart than suggested by experiment. 5 column-per-pore
+  systems stack, at a maximum, 0.9 \AA~further apart than experiment (see
+  Table~\ref{table:correlation_length}). The remainder of this discussion will
+  therefore focus on the analysis of systems built with 5 columns per pore.
 
@@
   \end{subfigure}
-  %MRSF: yellow not legended?
   \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
@@
 
-  %MRSF: I had a bit of hard time connecting the thesis of this paragraph to the details provided.
-  %BJCF: tried reorganizing a bit
   It therefore seems likely that the discrepancy between the shape and intensity of
@@
   highly correlated columns in our highly symmetric initial configurations.
-  %MRSF2: These next two sentences gets pretty confusing; too many clauses, if, when, since . . . make sentences shorter. 
   If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
   would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
-  average all $z$-slices of the 3D correlation function since contributions to
+  average all $z$-slices of the 3D correlation function. Contributions to
   $g(z)$ from head groups in other columns within the same pore, and with head
@@
   (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
-  behavior with a correlation length that nearly triples to 12.4 $\pm$ 0.7 \AA.
+  behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
   (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
@@
   in a system where columns act independently.
-  %Since all columns in our initial
-  %configuration are started at the same $z$-coordinate, $g(z)$ on average exhibits
-  %correlation of head groups with other head groups within the same column, with
-  %head groups in other columns within the same pore, and with head groups in different pores.
-
-  %BJC9: Note that the magnitude of the correlation function is much lower than 
-  % in figure 10a. That's because many of the z-slices are zero when you include
-  % all of them.
+
   \begin{figure}
@@
   by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
-  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees
-  well with experiment, meaning the quenched configuration contains about the
-  right amount of disorder on the $xy$ plane. However, the relatively low quality
-  of the fit implies that the FWHM of a fixed Lorentzian fit to data from a 
-  single simulation might not be the best comparison to experiment and that 
-  some form of initial configuration dependence causes extra structure.
-  %BJCF: new ending to this paragraph (above) 
-  %may actually be different from experiment, and
-  %that the radial ordering of the head groups may benefit from further optimization.
+  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
+  with experiment, meaning the quenched configuration contains about the right
+  amount of disorder on the $xy$ plane. However, the relatively low quality of
+  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
+  simulation might not be the best comparison to experiment and that some form of
+  initial configuration dependence causes extra structure.
 
@@
 
-  %BJCF: broke giant paragraph into 3 paragraphs, adjusted theses
-  %MRSF2: broke up the sentence, check to make sure it makes sense.
   Since the dynamics of this system are slow, consequently most of our analysis
   has been focused on a set of quenched configurations with some structural
-  characteristics that do not vary significantly with time.  We therefore attempted to learn
-  more about their time-averaged structures by studying ensembles of shorter 
-  simulations started from more independent initial configurations. To do this, we created
-  ensembles of 40 simulations in both the parallel displaced and sandwiched 
-  configurations. We used the same equilibration scheme described in Section~\ref{section:equilibration}. 
-  However, we built the initial 
-  configurations with columns randomly displaced in the $z$-direction and looked at
-  the results after 5 ns of unrestrained simulation, which should capture any 
-  quenched disorder built in from the initial configurations. We then simulated
-  XRD patterns from the 40 trajectories, concatenated together. The $q_r$ 
-  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
-  in Figure~\ref{fig:ensemble_XRD}.
+  characteristics that do not vary significantly with time. We therefore
+  attempted to learn more about their time-averaged structures by studying
+  ensembles of shorter simulations started from more independent initial
+  configurations. To do this, we created ensembles of 40 simulations in both the
+  parallel displaced and sandwiched configurations. We used the same
+  equilibration scheme described in Section~\ref{section:equilibration}.
+  However, we built the initial configurations with columns randomly displaced in
+  the $z$-direction and looked at the results after 5 ns of unrestrained
+  simulation, which should capture any quenched disorder built in from the
+  initial configurations. We then simulated XRD patterns from the 40
+  trajectories, concatenated together. The $q_r$ cross-sections of R-$\pi$
+  generated from the two concatenated trajectories are shown in
+  Figure~\ref{fig:ensemble_XRD}.
 
@@
 
-  %MRSF: is this the clearest thesis?
-Similar to each other?
-Similar to the amount of disordered viewed in the long simulations?
-Is the symmetric nature more useful?
-I think also this paragraph should be split up more to emphasize findings.
-  %BJCF: thesis changed, added reminder of initial randomization.
-  These short independent simulations exhibit a symmetric distribution of quenched
-  disorder providing evidence that the quenched disorder is randomized in each system. 
-  The only difference between each independent initial configuration
-  is the random $z$-direction displacement that we apply to each column. The
-  quenched disorder is then a result of the initial structural collapse that is 
-  directed by the randomized velocity vectors of the system's atoms drawn from
-  a Maxwell-Boltzmann distribution. We pooled the deviations of each head group COM 
-  from idealized positions from all independent simulations in order to create the 
-  distributions shown in Figure~\ref{fig:offset_ensemble_pooled} (see Section~\ref{method:simple_systems}).
-  The distributions appear symmetric meaning that there is an equal chance for a head
-  group to displace in the positive or negative $z$, $r$, or $\theta$-direction.
-
-  %BJCF: broke into separate paragraph
-  We verified that this same symmetry exists for individual COMs.
-  If we consider the COM of a given head group, we expect that the distribution of
-  its deviations from its idealized position among all the independent simulations
+  These short independent simulations exhibit a symmetric distribution of
+  quenched disorder providing evidence that the quenched disorder is randomized
+  in each system.  The only difference between each independent initial
+  configuration is the random $z$-direction displacement that we apply to each
+  column. The quenched disorder is then a result of the initial structural
+  collapse that is directed by the randomized velocity vectors of the system's
+  atoms drawn from a Maxwell-Boltzmann distribution. We pooled the deviations of
+  each head group COM from idealized positions from all independent simulations
+  in order to create the distributions shown in
+  Figure~\ref{fig:offset_ensemble_pooled} (see
+  Section~\ref{method:simple_systems}). The distributions appear symmetric
+  meaning that there is an equal chance for a head group to displace in the
+  positive or negative $z$, $r$, or $\theta$-direction.
+
+  We verified that this same symmetry exists for individual COMs.  If we
+  consider the COM of a given head group, we expect that the distribution of its
+  deviations from its idealized position among all the independent simulations
   should be symmetric about its idealized position. We can calculate the
@@
   deviations. The ECDFs of 3 randomly selected COMs are shown in
-  Figure~\ref{fig:offset_ecdfs} to guide the eye (colored lines). The average 
-  of all COM ECDFs is represented by the red line with the 95\% confidence
-  interval represented by the red error bars. We also calculated 
-  the ECDF from the full distributions in Figure~\ref{fig:offset_ensemble_pooled}
-  (black line with error bars). We generated error bars that represent the 95\% 
-  confidence intervals by performing 1000 trials where we randomly sampled 40
-  values (the same as the number of independent simulations) from the distributions in 
+  Figure~\ref{fig:offset_ecdfs} to guide the eye (colored lines). The average of
+  all COM ECDFs is represented by the red line with the 95\% confidence interval
+  represented by the red error bars. We also calculated the ECDF from the full
+  distributions in Figure~\ref{fig:offset_ensemble_pooled} (black line with error
+  bars). We generated error bars that represent the 95\% confidence intervals by
+  performing 1000 trials where we randomly sampled 40 values (the same as the
+  number of independent simulations) from the distributions in
   Figure~\ref{fig:offset_ensemble_pooled}, then measured the deviation between
   the sampled ECDF and the full ECDF. These error bars are generally smaller than
-  those generated from the 400 COM ECDFs, as there is a wider
-  distribution of mean COM deviations than the mean deviations from distributions
-  sampled from the full distribution. The similarity between entirely independently
-  sampled ECDFs and the ECDFs from individual independent simulations supports 
-  the hypothesis that each quenched configuration is random and mostly independent.
+  those generated from the 400 COM ECDFs, as there is a wider distribution of
+  mean COM deviations than the mean deviations from distributions sampled from
+  the full distribution. The similarity between entirely independently sampled
+  ECDFs and the ECDFs from individual independent simulations supports the
+  hypothesis that each quenched configuration is random and mostly independent.
 
@@
   differences between different possible structures studied here.
-
-  %MRSF: seems like a thesis w/o supporting data - maybe merge paragraphs, or provide a survey of the findings presented below.
-  %BJC: merged above
 
@@
 
-  We observe slow dynamics in our system. Typical diffusion constants for columnar
-  liquid crystals have been reported to be between $10^{-11}~ \mathrm{m}^2/\mathrm{s}$ 
-  \cite{dong_translational_1984} and $10^{-14}~\mathrm{m}^2/\mathrm{s}$ \cite{dvinskikh_molecular_2002}. 
-  %MRSF: see below comment; if not LLC's we should qualify this (electrostatics would likely make slower, since larger
-  %energies involved.
-  %MRS13: are these hydrophilic/hydrophopic LC?  Ones with electrostatic driving forces are likely 
-  % to be even slower.  
-  %BJCF: new addtion
-  In the case of LLCs, we would expect a diffusion coefficient at the low end of this
-  range since hydrophilic regions of monomers can hydrogen bond, thus increasing the energetic 
-  barriers for motion. We measured the diffusion constants of monomers in each of the main 
-  systems we studied (see Table \ref{S-table:msd} of the SI) and find they are all on the 
-  order of $10^{-14}~\mathrm{m}^2/\mathrm{s}$. However, since on this timescale, no monomers 
-  move a full `level' above or below, this may be an overestimate. This slow speed is
-  not entirely surprising considering how densely the monomers are packed as implied
-  by diffraction experiments. The entangled tails likely restrict both vertical and lateral
-  movement.
-
-  Consequently, there is not enough movement on the timescales we simulated for the system to 
-  consistently reach a definitive equilibrium structure. In all cases our monomers
-  equilibrate to a stacking distance that is too large compared to experiment. 
-  As discussed in Section~\ref{section:rpi}, while this may be in large part due to the 
-  force field's inability to model aromatic interactions, it is also possible that the
-  monomer tails do have enough time to pack as tightly as they could. More densely packed
-  tails could allow the monomers to stack closer together.
+  We observe slow dynamics in our system. Typical diffusion constants for
+  columnar liquid crystals have been reported to be between $10^{-11}~
+  \mathrm{m}^2/\mathrm{s}$ \cite{dong_translational_1984} and
+  $10^{-14}~\mathrm{m}^2/\mathrm{s}$ \cite{dvinskikh_molecular_2002}.  In the
+  case of LLCs, we would expect a diffusion coefficient at the low end of this
+  range since hydrophilic regions of monomers can hydrogen bond, thus increasing
+  the energetic barriers for motion. We measured the diffusion constants of
+  monomers in each of the main systems we studied (see Table \ref{S-table:msd} of
+  the SI) and find they are all on the order of
+  $10^{-14}~\mathrm{m}^2/\mathrm{s}$. However, since on this timescale, no
+  monomers move a full `level' above or below, this may be an overestimate. This
+  slow speed is not entirely surprising considering how densely the monomers are
+  packed as implied by diffraction experiments. The entangled tails likely
+  restrict both vertical and lateral movement.
+
+  Consequently, there is not enough movement on the timescales we simulated for
+  the system to consistently reach a definitive equilibrium structure. In all
+  cases our monomers equilibrate to a stacking distance that is too large
+  compared to experiment.  As discussed in Section~\ref{section:rpi}, while this
+  may be in large part due to the force field's inability to model aromatic
+  interactions, it is also possible that the monomer tails do have enough time to
+  pack as tightly as they could. More densely packed tails could allow the
+  monomers to stack closer together.
 
@@
 
-%MRSF: get rid of google books id on ref 45.
   \clearpage
@@
   \begin{figure}
+  \includegraphics[width=4.5cm]{toc_image_final.pdf}
   \includegraphics[width=4.07cm]{toc_waxs.pdf}
-  \includegraphics[width=4.5cm]{toc_image_final.pdf}
  \end{figure}

### 2018-10-11 Ben_Manuscripts/structure_paper/Final_Draft.tex
New TOC graphic
Final read-through edits

@@
   Periodic, nanostructured porous polymer membranes made from the cross-linked
-  inverted hexagonal phase
-  of self-assembled lyotropic liquid crystals (LLCs) are a promising class of materials
-  for selective separations. In this work, we investigate an experimentally
-  characterized LLC polymer membrane using atomistic molecular modeling. In particular,
-  we compare simulated X-ray diffraction (XRD) patterns with experimental XRD data
-  to quantify and understand the differences between simulation and experiment.
-  We find that the nanopores are likely composed of 5 columns of stacked LLC monomers
-  which surround each hydrophilic core. Evidence suggests that these columns likely 
-  move independently of each other over longer time scales than accessible via atomistic simulation.
-  We also find that WAXS structural features previously attributed to monomer tail 
-  tilt is likely instead due to ordered tail packing. Although this system
-  has been reported as dry, we show that small amounts of water are necessary
-  to reproduce all features from the experimental XRD pattern due to
-  asymmetries introduced by hydrogen bonds between the monomer head groups and
-  water molecules. Finally, we explore the composition and structure of the nanopores
-  and reveal that there exists a composition gradient rather than an abrupt
-  partition between the hydrophilic and hydrophobic regions. A caveat is
+  inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
+  a promising class of materials for selective separations. In this work, we
+  investigate an experimentally characterized LLC polymer membrane using
+  atomistic molecular modeling. In particular, we compare simulated X-ray
+  diffraction (XRD) patterns with experimental XRD data to quantify and
+  understand the differences between simulation and experiment.  We find that the
+  nanopores are likely composed of 5 columns of stacked LLC monomers which
+  surround each hydrophilic core. Evidence suggests that these columns likely
+  move independently of each other over longer time scales than accessible via
+  atomistic simulation. We also find that WAXS structural features previously
+  attributed to monomer tail tilt is likely instead due to ordered tail packing.
+  Although this system has been reported as dry, we show that small amounts of
+  water are necessary to reproduce all features from the experimental XRD pattern
+  due to asymmetries introduced by hydrogen bonds between the monomer head groups
+  and water molecules. Finally, we explore the composition and structure of the
+  nanopores and reveal that there exists a composition gradient rather than an
+  abrupt partition between the hydrophilic and hydrophobic regions. A caveat is
   that the time scales of the dynamics are extremely long for this system,
@@
   careful examination of the metastable states observed in order to draw any
-  conclusions. The clearer picture of the nanoscopic structure of these 
-  membranes provided in this study will enable a better understanding of
-  the mechanisms of small molecule transport within these nanopores.
+  conclusions. The clearer picture of the nanoscopic structure of these membranes
+  provided in this study will enable a better understanding of the mechanisms of
+  small molecule transport within these nanopores.
 
@@
 
-  More highly selective nanoporous membranes would be extremely useful 
-  in performing complex aqueous separations with seawater and various 
-  types of wastewater. For example, Sodium chloride and boron in seawater
+  More highly selective nanoporous membranes would be extremely useful for
+% BJC: in --> for
+  performing complex aqueous separations with seawater and various types of
+  wastewater. For example, Sodium chloride and boron in seawater
   \cite{fritzmann_state---art_2007} and organic micropollutants found in
-  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} represent
-  just a few of the diverse contaminants of water sources. By efficiently
-  separating contaminants from feed solutions with highly selective membranes,
-  it is possible to reduce the number of required membrane passes and post-treatment steps
-  needed for a given filtration process \cite{werber_materials_2016}, thus
-  lowering energy requirements. Additionally, one can also extract valuable resources
-  from the feed streams. For example, flowback water produced during hydraulic
-  fracturing of shale formations contains dissolved species such as acetate whose
-  extraction has economic value \cite{dischinger_application_2017}.
+  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
+  represent just a few of the diverse contaminants of water sources. By
+  efficiently separating contaminants from feed solutions with highly selective
+  membranes, it is possible to reduce the number of required membrane passes and
+  post-treatment steps needed for a given filtration process
+  \cite{werber_materials_2016}, thus lowering energy requirements. Additionally,
+  one can also extract valuable resources from the feed streams. For example,
+  flowback water produced during hydraulic fracturing of shale formations
+  contains dissolved species such as acetate whose extraction has economic value
+  \cite{dischinger_application_2017}.
 
@@
   Ordered, nanostructured porous membrane materials have become an increasingly popular
-  research area for aqueous separations applications because they offer the 
+  research area for aqueous separation applications because they offer the
+  %BJC: separations --> separation 
   ability to control pore architecture at the molecular scale, thereby
   permitting the design of solute-specific separation membranes
-  \cite{humplik_nanostructured_2011}. However, their development has been 
-  limited by the ability to synthesize and scale various technologies. Graphene
-  sheets are atomically thick, which results in excellent water permeability but
-  defects during manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
-  Molecular dynamics (MD) simulations of carbon nanotubes have shown promise
-  \cite{humplik_nanostructured_2011}, but synthetic techniques are unable to
-  achieve scalable alignment and pore monodispersity
-  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Consequently, there is a
-  need for new materials that could provide scalable nanostructured porous membranes.
+  \cite{humplik_nanostructured_2011}. However, their development has been limited
+  by the ability to synthesize and scale various technologies. Graphene sheets
+  are atomically thick, which results in excellent water permeability but defects
+  during manufacturing severely impact selectivity
+  \cite{cohen-tanugi_multilayer_2016}.  Molecular dynamics (MD) simulations of
+  carbon nanotubes have shown promise \cite{humplik_nanostructured_2011}, but
+  synthetic techniques are unable to achieve scalable alignment and pore
+  monodispersity \cite{hata_water-assisted_2004,maruyama_growth_2005}.
+  Consequently, there is a need for new materials that could provide scalable
+  nanostructured porous membranes.
 
   Preliminary evidence has shown that cross-linked lyotropic liquid crystal
-  (LLC) membranes can be produced at moderate scale and may be capable of performing highly selective
-  separations. LLCs are amphiphilic molecules that have the ability to
-  self-assemble into porous nanostructures \cite{smith_ordered_1997} and can be
-  cross-linked to create mechanically strong membrane films with periodic pores on the
-  order of 1 nm in diameter \cite{zhou_supported_2005}. Unlike the pores in most commercial NF
-  membranes, polymeric LLC membrane pores are uniform in size because they are
-  formed by self-assembly. Since LLC polymer membranes lack an appreciable pore size distribution, they
-  inherently exhibit high selectivity due to their strict molecular weight
-  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
-  examined in this paper are salts, and therefore lead to Donnan exclusion of
-  ions in solution. The membrane gains a net surface charge when counterions from
-  the head groups that line the pore walls escape into the feed solution in an
-  effort to balance the gradients of concentration and electric potential
-  \cite{donnan_theory_1995}.
-
-  The feasibility of nanostructured LLC polymer membranes for selective separations has
-  been demonstrated using LLC monomers that form the type 1 bicontinuous cubic
-  (Q\textsubscript{I})
+  (LLC) membranes can be produced at moderate scale and may be capable of
+  performing highly selective separations. LLCs are amphiphilic molecules that
+  have the ability to self-assemble into porous nanostructures
+  \cite{smith_ordered_1997} and can be cross-linked to create mechanically strong
+  membrane films with periodic pores on the order of 1 nm in diameter
+  \cite{zhou_supported_2005}. Unlike the pores in most commercial NF membranes,
+  polymeric LLC membrane pores are uniform in size because they are formed by
+  self-assembly. Since LLC polymer membranes lack an appreciable pore size
+  distribution, they inherently exhibit high selectivity due to their strict
+  molecular weight cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the
+  LLC monomers examined in this paper are salts, and therefore lead to Donnan
+  exclusion of ions in solution. The membrane gains a net surface charge when
+  counterions from the head groups that line the pore walls escape into the feed
+  solution in an effort to balance the gradients of concentration and electric
+  potential \cite{donnan_theory_1995}.
+
+  The feasibility of nanostructured LLC polymer membranes for selective
+  separations has been demonstrated using LLC monomers that form the type 1
+  bicontinuous cubic (Q\textsubscript{I})
   \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
@@
   form the same hexagonal columnar structure which, in the literature, has been
-  referred to as the Col\textsubscript{h} thermotropic phase\cite{feng_scalable_2014}.
-  Q\textsubscript{I}-phase membranes consist of a tortuous network of three
-  dimensionally interconnected pores that prevent optimal through-plane
-  transport. In contrast, the densely packed, non-tortuous and uniform sized
-  pores of H\textsubscript{II}-phase membranes represent the ideal geometry for
-  achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.  However, the
-  hexagonally packed LC domains of the H\textsubscript{II}-phase
-  generally form mutually unaligned domains, which hurts membrane permeability.
-  This domain scale misalignment had inhibited further development of this technology,
-  and research efforts were focused on the Q\textsubscript{I} phase, whose geometry
-  does not require alignment~\cite{zhou_new_2007}.
+  referred to as the Col\textsubscript{h} thermotropic
+  phase\cite{feng_scalable_2014}. Q\textsubscript{I}-phase membranes consist of
+  a tortuous network of three dimensionally interconnected pores that prevent
+  optimal through-plane transport. In contrast, the densely packed, non-tortuous
+  and uniform sized pores of H\textsubscript{II}-phase membranes represent the
+  ideal geometry for achieving high solute
+  flux\cite{matyka_tortuosity-porosity_2008}. However, the hexagonally packed LC
+  domains of the H\textsubscript{II}-phase generally form mutually unaligned
+  domains, which hurts membrane permeability. This domain scale misalignment had
+  inhibited further development of this technology, and research efforts were
+  focused on the Q\textsubscript{I} phase, whose geometry does not require
+  alignment~\cite{zhou_new_2007}.
 
@@
 	exhibits wedge-like character. (d) Monomers stack on top of each other to
-	create columns with short range order then assemble into pores with  
+	create columns with short range order, then assemble into pores with 
+        %BJC: order --> order, (added comma) 
 	hydrophilic head groups (blue) facing towards the pore center. (e) The 
@@
   chemical space available to design monomers for creation of separation-specific
-  membranes. Useful molecular-level modeling should incorporate a detailed picture of the
-  nanoscopic pore structure, which is crucial to understanding the role of
-  monomer structure in solute transport and membrane design. 
-  Atomistic molecular dynamics simulations can provide the required level of detail
-  (Figure \ref{fig:detail}), assuming the force fields are sufficiently accurate.
-  With such an atomistic model, we can directly observe molecular-level solute
-  transport and suggest governing mechanisms. We can also observe how the choice of
-  head group interacts with solutes of interest. In addition, we can interchange
-  counterions which may influence both the pore size and the strength of the
-  Donnan potential.
-
-  In this study, we achieve a  more realistic atomistic description of hexagonal LLC
-  polymer membranes than, to our knowledge, has ever previously been created, and explore
-  what new structural information can be gained and what structure hypotheses are
-  supported by this model. We validate the results using as much experimental
-  information as possible. We are most interested in reproducing the conclusions
-  about structure drawn from small-angle X-ray scattering (SAXS) and wide-angle
-  X-ray scattering (WAXS) experiments, as well as in matching ionic conductivity
-  measurements \cite{feng_thin_2016}.
+  membranes. Useful molecular-level modeling should incorporate a detailed
+  picture of the nanoscopic pore structure, which is crucial to understanding the
+  role of monomer structure in solute transport and membrane design.  Atomistic
+  MD simulations can provide the required level of detail (Figure
+  \ref{fig:detail}), assuming the force fields are sufficiently accurate.  With
+  such an atomistic model, we can directly observe molecular-level solute
+  transport and suggest governing mechanisms. We can also observe how the choice
+  of head group interacts with solutes of interest. In addition, we can
+  interchange counterions which may influence both the pore size and the strength
+  of the Donnan potential.
+
+  In this study, we achieve a more realistic atomistic description of a
+  %BJC: of --> of a
+  hexagonal LLC polymer membranes than, to our knowledge, has ever previously
+  been created, and explore what new structural information can be gained and
+  what structure hypotheses are supported by this model. We validate the results
+  using as much experimental information as possible. We are most interested in
+  reproducing the conclusions about structure drawn from small-angle X-ray
+  scattering (SAXS) and wide-angle X-ray scattering (WAXS) experiments, as well
+  as in matching ionic conductivity measurements \cite{feng_thin_2016}.
 
@@
   In this paper, we perform molecular modeling of the Col\textsubscript{h}
-  thermotropic (i.e., solvent-free) assembly formed by Na-GA3C11. Compared to 
-  the lyotropic (i.e, solvent-containing) H\textsubscript{II} phase, the
+  thermotropic (i.e., solvent-free) assembly formed by Na-GA3C11. Compared to the
+  lyotropic (i.e, solvent-containing) H\textsubscript{II} phase, the
   Col\textsubscript{h} phase is a simpler starting point. The system is not
-  assembled in aqueous phase which allowed us to simulate longer timescales
-  by omitting the solvent in the simulations,
-  and there exists detailed experimental characterization of the fully aligned state,
-  including 2D-WAXS patterns (Figure~\ref{fig:WAXS}) that are useful for 
-  reconstructing structural data.
+  assembled in aqueous phase which allowed us to simulate longer timescales by
+  omitting the solvent in the simulations, and there exists detailed experimental
+  characterization of the fully aligned state, including 2D-WAXS patterns
+  (Figure~\ref{fig:WAXS}) that are useful for reconstructing structural data.
 
   There are five major features of interest present in the 2D experimental
-  pattern shown in Figure~\ref{fig:WAXS}.
+  WAXS pattern shown in Figure~\ref{fig:WAXS}.
 
@@
 	stacking between aromatic rings in the direction perpendicular to the membrane
-	plane, or z-axis \cite{feng_scalable_2014}. For simplicity, we will refer to
+	plane, or $z$-axis \cite{feng_scalable_2014}. For simplicity, we will refer to
 	this reflection as R-$\pi$.
@@
 	relative intensity.  Accordingly, we name these reflections R-spots. The
-	location of all spots is $\sim37^{\circ}$ from the $q_z$ axis in their
+	location of all spots is $\sim37^{\circ}$ from the $q_r$ axis in their
+	%BJC: q_z --> q_r
 	respective quadrants. In many liquid crystal systems, such spots are explained
@@
 
- 	Authors often describe this and similar systems as being made up of stacked monomer layers. A simple
- 	molecular simulation study of a similar molecule suggested that there are 4 monomers
- 	in each layer. Their estimation is based on a simulated system containing only 16 total
- 	monomers which likely does not sufficiently model the chemical environment present in
- 	the real system.~\cite{zhu_methacrylated_2006}. A separate calculation based on the 
- 	volume of the liquid crystal monomers proposes that there are seven monomers in each 
- 	layer~\cite{resel_structural_2000}.
-
-  	We are careful to avoid the term ``layers" since many liquid crystalline systems
- 	have long range order in 1 or 2 spatial dimensions and short range order in 	
- 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
- 	In the system we are studying, there are long-range 2D correlations in the 
- 	hexagonal array of pores (xy plane) and short range $z$-direction correlations within 
-    stacked columns of monomers. In this study, we use atomistic molecular modeling
-    to study how the system's structure is affected by the density of these monomer columns
-    that surround each pore's hydrophilic core.
+	Authors often describe this and similar systems as being made up of
+	stacked monomer layers. A simple molecular simulation study of a similar
+	molecule suggested that there are 4 monomers in each layer. Their estimation is
+	based on a simulated system containing only 16 total monomers which likely does
+	not sufficiently model the chemical environment present in the real
+	system.~\cite{zhu_methacrylated_2006}. A separate calculation based on the
+	volume of the liquid crystal monomers proposes that there are seven monomers in
+	each layer~\cite{resel_structural_2000}.
+
+	We are careful to avoid the term ``layers" since many liquid
+	crystalline systems have long range order in 1 or 2 spatial dimensions and
+	short range order in the other dimensions.~\cite{chaikin_principles_1995}  %
+	page 58 In the system we are studying, there are long-range 2D correlations in
+	the hexagonal array of pores ($xy$ plane) and short range $z$-direction
+	correlations within stacked columns of monomers. In this study, we use
+	atomistic molecular modeling to study how the system's structure is affected by
+	the density of these monomer columns that surround each pore's hydrophilic
+	core.
 
@@
 
-	On the short timescales accessible to MD (even the 100's of nanoseconds of simulation 
-	performed here are short compared to experimental timescales), we observe distinct metastable
-	configurations which depend on starting configuration. We simulated XRD patterns of our system and 
-	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS}) so that we ensure our
-	model creates a nanoscopic chemical environment maximally consistent with experiment within 
-	the constraints	of our force field. Using this approach, we are able to confirm some previous
-	interpretations	of the WAXS pattern and refute others.
+	On the short timescales accessible to MD (even the 100's of nanoseconds
+	of simulation performed here are short compared to experimental timescales), we
+	observe distinct metastable configurations which depend on starting
+	configuration. We simulated X-ray diffraction (XRD) patterns of our system and
+	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS}) so that
+	we ensure our model creates a nanoscopic chemical environment maximally
+	consistent with experiment within the constraints of our force field. Using
+	this approach, we are able to confirm some previous interpretations	of the
+	WAXS pattern and refute others.
 
@@
 	that small amounts of ambient water are absorbed into the system. The
-	hydrogen-bonding network formed by the water may play a role in structuring 
-	the pore. We used simulated X-ray diffraction (XRD) patterns to uncover any 
-	meaningful structural difference between a ``dry" and a ``wet" system.
+	hydrogen-bonding network formed by the water may play a role in structuring the
+	pore. We used simulated XRD patterns to uncover any meaningful structural
+	difference between a ``dry" and a ``wet" system.
 
@@
   \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Additional details are available in 
-  Section \ref{S-section:python_scripts} of the SI.
+  Section \ref{S-section:python_scripts} of the Supporting Information (SI).
 
@@
   construction. Section \ref{S-section:parameterization} 
-  of the Supporting Information (SI) provides further detail of the parameterization process.
+  of the SI provides further detail of the parameterization process.
 
@@
   requiring a more efficient way to build the system. Previous work has shown
-  a united-atom model of LLC can self-assemble into the H\textsubscript{II} phase
-  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
-  attempted atomistic self-assembly by packing monomers into a box using Packmol
-  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
-  indicators of progress towards an ordered system (see Section \ref{S-section:self_assembly} of the 
-  SI). To bypass the slow self-assembly process, we used a 
-  variety of automated procedures to assemble monomers into a structure close to
-  one of a number of hypothesized equilibrium configurations (See Figure 
-  \ref{S-fig:build_procedure} of the SI). These initial structures may result
-  in equilibration into slowly-intercoverting metastable states, an issue we will
-  address later in the paper.
+  that a united-atom model of an LLC can self-assemble into the
+  %BJC: show a united-atom --> that a united-atom ; of LLC --> of an LLC
+  H\textsubscript{II} phase configuration in $\sim$1000 ns
+  \cite{mondal_self-assembly_2013}. We attempted atomistic self-assembly by
+  packing monomers into a box using Packmol \cite{martinez_packmol:_2009}.
+  Simulations of greater than 100 ns show no indicators of progress towards an
+  ordered system (see Section \ref{S-section:self_assembly} of the SI). To bypass
+  the slow self-assembly process, we used automated procedures to
+  %BJC: a variety of automated --> automated
+  assemble monomers into a structure close to one of a number of hypothesized
+  equilibrium configurations (See Figure \ref{S-fig:build_procedure} of the SI).
+  These initial structures may result in equilibration into slowly-intercoverting
+  metastable states, an issue we will address later in the paper.
 
@@
   When constructing an initial configuration, there are a number of variables
-  which require careful consideration while placing monomers. We find that the equilibrium
-  configuration is sensitive to some while insensitive to others. For example, we find the starting
-  pore radius, defined as the distance of a chosen head group carbon from the
-  pore's central axis, does not influence the equilibrium structure if one chooses
-  a reasonable value. The initial distance between pores, within a wide range, also has 
-  little effect on the equilibrated structure. However, one should not start them
-  too close or there will be high energy repulsions during early equilibration. We chose a
-  pore radius of 0.5 nm and an initial pore spacing of 4.5 nm, $\sim$10\% larger than the 
-  experimental value of 4.12 nm for our initial configurations. A sensitivity analysis of 
-  both parameters is presented in the SI, Section \ref{S-section:initial_config_dependence}. The 
-  distance between vertically stacked monomers, the xy position of monomers with respect 
-  to vertically adjacent monomers, and the number of columns per pore do influence the 
-  equilibrated structure and require further justification for their choices. We rely on 
-  experimental data to inform them.
-
-  We chose the vertical spacing between monomers for the initial configuration based
-  on R-$\pi$ and then allowed the system to readjust during equilibration. We rotated 
-  each monomer so the plane of its aromatic head group would be coplanar with the xy plane. We
-  explored three different initial monomer spacings. The first is exactly
-  equal to R-$\pi$ with monomers placed so aromatic rings stack 3.7 \AA~apart in
-  the $z$-direction. We also extensively explored a second system with an initial spacing of 5
-  \AA. We briefly explored a third system with an initial spacing of 10
-  \AA. However this largest spacing yields non-physical behavior which is detailed in the 
-  SI, Section \ref{S-section:initial_dbwl}.
+  which require careful consideration while placing monomers. We find that the
+  equilibrium configuration is sensitive to some while insensitive to others. For
+  example, we find the starting pore radius, defined as the distance of a chosen
+  head group carbon from the pore's central axis, does not influence the
+  equilibrium structure if one chooses a reasonable value. The initial distance
+  between pores, within a wide range, also has little effect on the equilibrated
+  structure. However, one should not start them too close or there will be high
+  energy repulsions during early equilibration. We chose a pore radius of 0.5 nm
+  and an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental
+  value of 4.12 nm for our initial configurations. A sensitivity analysis of both
+  parameters is presented in the SI, Section
+  \ref{S-section:initial_config_dependence}. The distance between vertically
+  stacked monomers, the $xy$ position of monomers with respect to vertically
+  adjacent monomers, and the number of columns per pore do influence the
+  equilibrated structure and require further justification for their choices. We
+  rely on experimental data to inform them.
+
+  We chose the vertical spacing between monomers for the initial configuration
+  based on R-$\pi$ and then allowed the system to readjust during equilibration.
+  We rotated each monomer so the plane of its aromatic head group would be
+  coplanar with the $xy$ plane. We explored three different initial monomer
+  spacings. The first is exactly equal to R-$\pi$ with monomers placed so
+  aromatic rings stack 3.7 \AA~apart in the $z$-direction. We also extensively
+  explored a second system with an initial spacing of 5 \AA. We briefly explored
+  a third system with an initial spacing of 10 \AA. However this largest spacing
+  yields non-physical behavior which is detailed in the SI, Section
+  \ref{S-section:initial_dbwl}.
 
@@
   based on clues from diffraction data as well as the various known stacking modes of 
-  benzene and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
+  benzene and substituted benzene rings: sandwiched, parallel displaced and T-shaped
   \cite{sinnokrot_estimates_2002}. We ruled out the T-shaped configuration
@@
   To calculate the equilibrated pore spacing, we measured the distance between
-  pore centers. We located the pore centers by averaging the coordinates of sodium
-  ions in their respective pores. We generated pore spacing statistics 
+  pore centers. We located the pore centers by averaging the coordinates of
+  sodium ions in their respective pores. We generated pore spacing statistics
   using the bootstrapping technique (See Section \ref{S-section:p2p_stats} of the
-  SI). 
-  The pore spacings calculated in this way are consistent
-  with one half of the $x$ and $y$ box vectors (See, Table \ref{S-table:p2p} in the
-  SI). However, our method for their calculation does a better 
-  job capturing the spread of pore-to-pore distances.
+  SI). The pore spacings calculated in this way are consistent with one half of
+  the $x$ and $y$ box vectors (See Table \ref{S-table:p2p} in the SI). However,
+  our method for their calculation does a better job capturing the spread of
+  pore-to-pore distances.
 
@@
   the alkane-alkane density, averaged over all angles, is the feature most likely
-  to be replicated between experiment and simulation, as atomistic alkane
-  force field parameters are relatively well-studied. Other features are dependent on system
-  ordering which is likely to have some dependence on initial configuration.  We
-  calculated the average intensity within R-alkanes of the experimental pattern,
-  $I_{avg}$ and divided all intensities by this value. In this way, the average
-  intensity of R-alkanes was set equal to 1. When calculating $I_{avg}$, we excluded
-  intensities within $\pm$30\degree~of the meridional axis defined by $q_r=0$,
-  since the simulated patterns differ from experiment in those regions in all
-  cases (See Figure~\ref{fig:ralkanes}). Specifically, in contrast to the
-  experimental WAXS pattern, R-$\pi$, as it appears in the simulated diffraction
-  patterns, intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set an
-  upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$.
-  Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored
-  uniformly.  We applied the same scaling method to the simulated patterns. We
-  chose a scaling factor of $f=3.1$ in order to visibly display all
-  features in all patterns.
+  to be replicated between experiment and simulation, as atomistic alkane force
+  field parameters are relatively well-studied~\cite{wang_development_2004}.
+  Other features are dependent on system ordering which is likely to have some
+  dependence on initial configuration.  We calculated the average intensity
+  within R-alkanes of the experimental pattern, $I_{avg}$, and divided all
+  intensities by this value. In this way, the average intensity of R-alkanes was
+  set equal to 1. When calculating $I_{avg}$, we excluded intensities within
+  $\pm$30\degree~of the meridional axis defined by $q_r=0$, since the simulated
+  patterns differ from experiment in those regions in all cases (See
+  Figure~\ref{fig:ralkanes}). Specifically, in contrast to the experimental WAXS
+  pattern, R-$\pi$, as it appears in the simulated diffraction patterns,
+  intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set an upper bound
+  on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$.  Intensities
+  that appear in the patterns $\geq$ $f\times I_{avg}$ are colored uniformly.  We
+  applied the same scaling method to the simulated patterns. We chose a scaling
+  factor of $f=3.1$ in order to visibly display all features in all patterns.
 
@@
   the R-alkanes region. We took the intensity of R-spots as the average of the 
-  peak intensities near -37 and -143$\degree$. (d) We measured the intensity of 
+  peak intensities near 37 and 143$\degree$. (d) We measured the intensity of 
   R-pores by measuring the height of the d\textsubscript{100} peak (the leading
@@
   We measured the one dimensional pair distribution function, $g(z)$, between centers 
-  of masses (COM) of aromatic head group rings along the $z$-axis (perpendicular to
+  of masses (COMs) of aromatic head group rings along the $z$-axis (perpendicular to
   the membrane plane). We averaged all 1D $z$-directional slices of the full 3D 
@@
 
-  In order to gain a deeper understanding of discrepancies between the experimental and
-  simulated R-$\pi$ reflection, we used a simplified model where we 
-  represent each monomer as a single point scatterer located at the COM
-  of its head group. In order to make a system approximately similar to our equilibrated 
-  simulation geometries, we created 4 hexagonally packed pore regions spaced 42.5 \AA~
-  apart, each with 5 columns of scatterers spaced 4.4 \AA~apart in the $z$-direction. We
-  built the system 4 times taller in the $z$-direction (80 scatterers per column) in order
-  to access higher $q_z$ resolution.
-
-  We gave the simplified models the same amount of disorder present in the atomistic
-  simulations. We observe two sources of disorder in our atomistic simulations: thermal motion of atoms
-  during the simulation and quenched disorder created by rapid structural rearrangement during 
-  early equilibration and is largely locked into place for the remainder of the 
-  simulation, even at the 100 ns time scale. We measured thermal disorder by calculating the standard deviation of 
-  the distribution of head group COM positions from their average positions.
-  We measured quenched disorder by calculating the standard deviation of the distribution
-  of head group COMs from their idealized average positions. In the 
-  $z$-direction, we measured the deviation of the head group COMs from an
-  equally spaced column of head groups. In the $xy$ plane, we calculated the standard 
-  deviation in radial position from the pore center and the angular deviation from 
-  equally spaced points surrounding the pore center. This method for calculating 
-  quenched disorder inherently includes the convoluted thermal disorder.
+  In order to gain a deeper understanding of discrepancies between the
+  experimental and simulated R-$\pi$ reflection, we used a simplified model where
+  we represent each monomer as a single point scatterer located at the COM of its
+  head group. In order to make a system approximately similar to our equilibrated
+  simulation geometries, we created 4 hexagonally packed pore regions spaced 42.5
+  \AA~ apart, each with 5 columns of scatterers spaced 4.4 \AA~apart in the
+  $z$-direction. We built the system 4 times taller in the $z$-direction (80
+  scatterers per column) in order to access higher $q_z$ resolution.
+
+  We gave the simplified models the same amount of disorder present in the
+  atomistic simulations. We observe two sources of disorder in our atomistic
+  simulations: thermal motion of atoms during the simulation and quenched
+  disorder created by rapid structural rearrangement during early equilibration
+  that is largely locked into place for the remainder of the simulation, even at
+  %BJC: and --> that
+  the 100 ns time scale. We measured thermal disorder by calculating the standard
+  deviation of the distribution of head group COM positions from their average
+  positions. We measured quenched disorder by calculating the standard deviation
+  of the distribution of head group COMs from their idealized average positions.
+  In the $z$-direction, we measured the deviation of the head group COMs from an
+  equally spaced column of head groups. In the $xy$ plane, we calculated the
+  standard deviation in radial position from the pore center and the angular
+  deviation from equally spaced points surrounding the pore center. This method
+  for calculating quenched disorder inherently includes the convoluted thermal
+  disorder.
 
@@
 
-  Our simulations best support a model built with 5 monomer columns per pore based on
-  the measured equilibrated pore-to-pore distances. To identify the density of
-  monomer columns around each pore, addressing question \ref{point:monomernum} in the introduction, we ran
-  simulations of systems created with 4--8 columns per pore. We built systems in both
-  the parallel displaced and sandwiched configurations and equilibrated them according
-  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
-  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional 
-  systems with monomers initially spaced 5 \AA~apart vertically (see Section \ref{S-section:initial_pore_spacing}
-  of the SI for more details on sensitivity to initial monomer spacing). 
-  We considered the pore-to-pore spacing to be equilibrated as defined in Section~\ref{method:equil_time}.
-  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested.
+  Our simulations best support a model built with 5 monomer columns per pore
+  based on the measured equilibrated pore-to-pore distances. To identify the
+  density of monomer columns around each pore, addressing Question
+  \ref{point:monomernum} in the introduction, we ran simulations of systems
+  created with 4--8 columns per pore. We built systems in both the parallel
+  displaced and sandwiched configurations and equilibrated them according to the
+  dry equilibration procedure. We tested all systems with an initial vertical
+  monomer spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested
+  4 additional systems with monomers initially spaced 5 \AA~apart vertically (see
+  Section \ref{S-section:initial_pore_spacing} of the SI for more details on
+  sensitivity to initial monomer spacing). We considered the pore-to-pore
+  spacing to be equilibrated as defined in Section~\ref{method:equil_time}.
+  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all
+  systems tested.
 
@@
 
-  All systems tested, although equilibrated from the perspective of the metrics used here, are
-  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
-  we are trying to match. In the limit of infinite simulation time, all systems will in theory 
-  converge to a single equilibrium configuration, but that time is far beyond the 100's of 
-  nanosecond simulated here. For simplicity, we group the systems studied here into the ordered
-  and disordered basins. What we find is that any system equilibrated with $\mathit{d}=3.7$ \AA~can generally 
-  be characterized as being in a more ordered basin, and any system equilibrated with $\mathit{d}=5.0$ \AA~can
-  be characterized as begin in a more disordered basin. The extra space between stacked monomers
-  in the disordered basin systems gives the monomer head groups more rotational freedom. We 
-  quantified the ordering of the head groups using the nematic order parameter (see Section 
-  \ref{S-method:nematic_order} for details of the calculation). Disordered basin systems have
-  a lower nematic order parameter (meaning they are more disordered) than ordered basin systems. 
-  Generally, when monomers are started further apart, they stay further apart than systems where
-  monomers are started closer together (see Table~\ref{table:correlation_length}). This increased
-  equilibrated stacking distance of monomers in disordered basin systems increases their discrepancy
-  with experimental stacking distances derived from WAXS relative to ordered basin systems 
-  (See Section~\ref{section:rpi}).
+  All systems tested, although equilibrated from the perspective of the metrics
+  used here, are frozen in metastable basins. Not all make physical sense or fit
+  the experimental profile that we are trying to match. In the limit of infinite
+  simulation time, all systems will in theory converge to a single equilibrium
+  configuration, but that time is far beyond the 100's of nanoseconds simulated
+  here. For simplicity, we group the systems studied here into the ordered and
+  disordered basins. What we find is that any system equilibrated with
+  $\mathit{d}=3.7$ \AA~can generally be characterized as being in a more ordered
+  basin, and any system equilibrated with $\mathit{d}=5.0$ \AA~can be
+  characterized as being in a more disordered basin. The extra space between
+  stacked monomers in the disordered basin systems gives the monomer head groups
+  more rotational freedom. We quantified the ordering of the head groups using
+  the nematic order parameter (see Section \ref{S-method:nematic_order} for
+  details of the calculation). Disordered basin systems have a lower nematic
+  order parameter (meaning they are more disordered) than ordered basin systems.
+  Generally, when monomers are started further apart, they stay further apart
+  than systems where monomers are started closer together (see
+  Table~\ref{table:correlation_length}). This increased equilibrated stacking
+  distance of monomers in disordered basin systems increases their discrepancy
+  with experimental stacking distances derived from WAXS relative to ordered
+  basin systems (See Section~\ref{section:rpi}).
 
@@
   disordered basin systems built with 6 columns-per-pore agree with experimental
-  pore-to-pore distances within error, but stack too far apart.  Monomers in 6
-  column-per-pore disordered sandwiched and disordered parallel displaced
+  pore-to-pore distances within error, but stack too far apart. 6
+  %BJC: Monomers in 6 --> 6
+  column per pore disordered sandwiched and disordered parallel displaced
   configurations stack $\sim$~4.87 and 4.94 \AA~apart respectively, which is
@@
   patterns produced from equilibrated MD trajectories (see
-  Section~\ref{method:xrd}) and comparing these simulated patters to experiment, addressing
-  question~\ref{point:xrdmatch} in the introduction. We tested systems built with 5 columns per pore
-  in the parallel displaced and sandwiched configurations at
-  300 K in the ordered and disordered basins, as those were the most consistent
-  with the most unambiguous XRD features, the pore-to-pore spacing
-  and the stacking distance, as described in Section~\ref{section:mon_per_pore}. 
-  We generated simulated patterns using the locally
-  equilibrated portion of each simulation trajectory (see
+  Section~\ref{method:xrd}) and comparing these simulated patterns to experiment,
+  addressing Question~\ref{point:xrdmatch} in the Introduction. We tested systems
+  built with 5 columns per pore in the parallel displaced and sandwiched
+  configurations at 300 K in the ordered and disordered basins, as those were the
+  most consistent with the most unambiguous XRD features, the pore-to-pore
+  spacing and the stacking distance, as described in
+  Section~\ref{section:mon_per_pore}.  We generated simulated patterns using the
+  locally equilibrated portion of each simulation trajectory (see
   Section~\ref{method:equil_time}). There are two important factors to take into
-  account when looking at differences between experimental and simulated XRD patterns.
-  First, the simulated diffraction patterns have some noise, especially along the
-  $q_z$ axis at $q_r$=0, which is where several of the more interesting features
-  are located. This is due to the angle averaging of the 3D structure factor
-  around the $q_z$-axis, meaning there are fewer samples as $q_r$ approaches 0.
-  More importantly, our simulations do not appear to be long enough to sample truly
-  independent configurations within their respective metastable basins (see
-  Section~\ref{section:slow_dynamics}), meaning we must take care in interpreting
-  the results of the XRD. The amount of independent configurations required to 
-  converge along the $q_z$ axis is analyzed in SI, 
+  account when looking at differences between experimental and simulated XRD
+  patterns.  First, the simulated diffraction patterns have some noise,
+  especially along the $q_z$ axis at $q_r$=0, which is where several of the more
+  interesting features are located. This is due to the angle averaging of the 3D
+  structure factor around the $q_z$-axis, meaning there are fewer samples as
+  $q_r$ approaches 0.  More importantly, our simulations do not appear to be long
+  enough to sample truly independent configurations within their respective
+  metastable basins (see Section~\ref{section:slow_dynamics}), meaning we must
+  take care in interpreting the results of the XRD. The amount of independent
+  configurations required to converge along the $q_z$ axis is analyzed in SI,
   Section \ref{S-section:xrd_noise}. The simulated patterns generated for all
-  systems studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.
+  systems studied are shown and compared to experiment in
+  Figure~\ref{fig:XRDsim}.
 
@@
 		interest are presented in Table~\ref{table:relative_intensities_300K}. In both
-		XRD patterns generated from parallel displaced patterns, there is a faint line
+		XRD patterns generated from parallel displaced configurations, there is a faint line
 		across $q_z \sim 0.7~$\AA$^{-1}$, half the simulated value of R-$\pi$. Although
@@
   simulations. We reached this conclusion because alkane parameters in GAFF and
-  AMBER forcefields generally reproduce data well.~\cite{wang_development_2004,caleman_force_2012}
+  AMBER forcefields generally reproduce data
+  well.~\cite{wang_development_2004,caleman_force_2012}
 
@@
   estimate its location, appears at a $|\mathbf{q}|$ value that is, at most,
-  3.5\% higher than higher than experiment. The error in the simulated 
-  diffraction patterns is less than the error due binning in each frequency
-  direction, so was not further investigated.
+  3.5\% higher than experiment. The error in the simulated diffraction patterns
+  is less than the error due binning in each frequency direction, so was not
+  further investigated.
 
@@
 
+  In order to more clearly identify the structural reasons for R-spots, we
+  equilibrated an ordered basin sandwiched configuration at 280 K to moderately
+  increase the order and therefore intensity. Many force fields do not obtain
+  the correct equilibrium structure at precisely the experimental temperature.
+  Wang et al. highlighted the shortcoming of some of the most popular protein
+  force fields in predicting the temperature dependence of protein structural
+  ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
+  our membrane system, simulated at 300 K, is under-structured in the tail region
+  compared to the experimental structure at 300 K. We found that lowering the
+  temperature indeed better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
+  suggesting that our `effective' temperature might indeed be too high,
+  understabilizing structure.
+
   Previous literature has attributed the R-spots reflection in this particular
@@
 
-  In order to more clearly identify the structural reasons for R-spots, we
-  equilibrated an ordered basin sandwiched configuration at 280 K to moderately
-  increase the order and therefore intensity.  Many force fields do not obtain
-  the correct equilibrium structure at precisely the experimental temperature.
-  Wang et al. highlighted the shortcoming of some of the most popular protein
-  force field in predicting the temperature dependence of protein structural
-  ensembles \cite{wang_building_2017}. It is therefore possible that   % page 12
-  our membrane system, simulated at 300 K, is under-structured in the tail region
-  compared to the experimental structure at 300 K. We found that lowering the
-  temperature indeed better resolved R-spots (Figure~\ref{fig:sandwiched280K}),
-  suggesting that our `effective' temperature might indeed be too high,
-  understabilizing structure.
-
-  The evidence from simulations strongly suggest that the source of
-  the R-spots reflection is packing of the tails in a hexagonal array.
-  First, we demonstrate R-spots comes primarily from the tails, by
-  removing all non-tail atoms from the trajectory and simulating the
-  XRD diffraction pattern with the remaining atoms, which preserves
-  R-spots (Figure~\ref{fig:tails_rzplot}).  Next, we plotted the center
+  The evidence from simulations strongly suggest that the source of the R-spots
+  reflection is packing of the tails in a hexagonal array.  First, we demonstrate
+  R-spots comes primarily from the tails, by removing all non-tail atoms from the
+  trajectory and simulating the XRD pattern with the remaining atoms, which
+  preserves R-spots (Figure~\ref{fig:tails_rzplot}).  Next, we plotted the center
   of masses of the first four tail atoms of all tails (Figure
-  \ref{fig:centroids}). We measured the angle between each COM
-  and its nearest neighbor COMs with respect to the
-  $xy$ plane of the membrane. We see distinct peaks in the
-  distribution of these angles located ca. $-60\degree$, $0\degree$,
-  and $60\degree$, which is consistent with a hexagonally-packed
-  configuration (Figure~\ref{fig:layered_tails}).  This ordering is
-  primarily in the parts of the tail proximal to the heads, and dies
-  off at the tail ends, where there is more space to fill causing them
-  to pack nearly isotropically. See Section \ref{S-section:tail_packing} 
-  of the SI for
-  a more detailed explanation of the calculation and packing
-  distributions generated from different sections of the tails.
+  \ref{fig:centroids}). We measured the angle between each COM and its nearest
+  neighbor COMs with respect to the $xy$ plane of the membrane. We see distinct
+  peaks in the distribution of these angles located ca. $-60\degree$, $0\degree$,
+  and $60\degree$, which is consistent with a hexagonally-packed configuration
+  (Figure~\ref{fig:layered_tails}).  This ordering is primarily in the parts of
+  the tail proximal to the heads, and dies off at the tail ends, where there is
+  more space to fill causing them to pack nearly isotropically. See Section
+  \ref{S-section:tail_packing} of the SI for a more detailed explanation of the
+  calculation and packing distributions generated from different sections of the
+  tails.
 
@@
   \caption{(a) R-spots increases in intensity when the temperature of the system is 
-      lowered to 280K. (b) We measured the average angle made between each monomer 
-      alkane tail and the membrane plane. The average tilt angle (dashed line) is 
-      near -2\degree~which is far from the 37\degree~tilt angle previously used to
-      explain R-spots. (c) To isolate the main cause of R-spots, we removed all atoms
-      from the trajectory except for carbon atoms that constitute the tails. The
-      simulated XRD pattern of the tails-only trajectory still shows R-spots. (d)
-      Since the tails stay relatively flat, we plotted the center of mass of the first
-      four carbon atoms of each tail originating from the head groups (for example,
-      green colored centroids in the plot surround the red centroid in hexagonal fashion).
-      Visually, the packing looks hexagonal. (e) We hypothesize
-      that R-spots is the result of ordered tail packing. Defining
-      the membrane plane to be 0\degree, we measured the angles between each center of 
-      mass and its nearest neighbor center of masses for the equilibrated 
-      sandwiched configuration simulated at 280K. Peaks appear in the distribution at 
-      $-60\degree$, $0\degree$ and $60\degree$. (f) The Fourier transform of a hexagonally
-      packed grid of points defined by the angles in (e) shows intensity at the same
-      locations where we expect to see R-spots, as well as intensity along the $q_z$ axis
+	  lowered to 280 K. (b) We measured the average angle made between each
+	  monomer alkane tail and the membrane plane. The average tilt angle (dashed
+	  line) is near -2\degree~which is far from the 37\degree~tilt angle previously
+	  used to explain R-spots. (c) To isolate the main cause of R-spots, we removed
+	  all atoms from the trajectory except for carbon atoms that constitute the
+	  tails. The simulated XRD pattern of the tails-only trajectory still shows
+	  R-spots. (d) Since the tails stay relatively flat, we plotted the center of
+	  mass of the first four carbon atoms of each tail originating from the head
+	  groups (for example, green colored centroids in the plot surround the red
+	  centroid in hexagonal fashion).  Visually, the packing looks hexagonal. (e) We
+	  hypothesize that R-spots is the result of ordered tail packing. Defining the
+	  membrane plane to be 0\degree, we measured the angles between each COM and its
+	  nearest neighbor COMs for the equilibrated sandwiched configuration simulated
+	  at 280 K. Peaks appear in the distribution at $-60\degree$, $0\degree$ and
+	  $60\degree$. (f) The Fourier transform of a hexagonally packed grid of points
+	  defined by the angles in (e) shows intensity at the same locations where we
+	  expect to see R-spots, as well as intensity along the $q_z$ axis
           where R-$\pi$ would appear.}~\label{fig:tail_packing}
@@
   The position, shape, and intensity of R-$\pi$, generated from simulations at
-  300 K have qualitative and quantitative differences from experiment.
-  The reflections appear at lower $q_z$ values, they
-  are more intense, and the shape of its cross-sections, especially in the $q_r$
-  direction are different relative to the experimental system.  For comparison,
-  see Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the
+  300 K have qualitative and quantitative differences from experiment. The
+  reflections appear at lower $q_z$ values, they are more intense, and the shape
+  of its cross-sections, especially in the $q_r$ direction are different relative
+  to the experimental system. For comparison, see
+  Figure~\ref{fig:rpi_exp_comparison} where we used cross-sections of the
   simulated XRD generated from the ordered parallel displaced configuration as an
@@
   discrepancies, and use this information to speculate on what reasonable
-  differences in the simulations could explain the discrepancies.
+  differences in the simulations could explain them.
 
@@
 	  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
-  the FWHM (full width at half maximum) of the simulated pattern agrees with experiment within error. However
-  the fit to the simulated data is affected by the three sharp peaks which appear
-  near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
-  qualitatively similar. Each fits a Lorentzian profile well, however the FWHM
-  of the simulated cross-section (d) is 48\% larger than the experimental 
-  cross-section. Additionally, the peak of the simulated $q_z$ cross-section is 
-  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
+	  the FWHM (full width at half maximum) of the simulated pattern agrees with
+	  experiment within error. However the fit to the simulated data is affected by
+	  the three sharp peaks which appear near $q_r$ = 0. The $q_z$ cross-sections of
+	  R-$\pi$ ((c) and (d)) are qualitatively similar. Each fits a Lorentzian profile
+	  well, however the FWHM of the simulated cross-section (d) is 48\% larger than
+	  the experimental cross-section (c). Additionally, the peak of the simulated
+	  $q_z$ cross-section is located at a lower $q_z$ value than
+	  experiment.}\label{fig:rpi_exp_comparison}
   \end{figure}
@@
 
-  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment because
-  monomers in the simulated system stack further apart than those in the experimental
-  system (Table~\ref{table:correlation_length}). We calculated $z$-direction pair distribution
-  functions, $g(z)$, as described in Section~\ref{section:correlation_length}.
-  The resulting distributions are generally characterized by decaying
-  oscillatory behavior where the average distance between peaks corresponds to
-  the average distance between stacked monomer head groups
-  (Figure~\ref{fig:correlation}).  We calculated this equilibrated vertical
-  stacking distance, $\mathit{d}_{equil}$, between monomers using
-  Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked monomers is
-  greater than experiment by 0.5--0.9 \AA~across all cases, with disordered
-  basins at the high end of that range.% and are on average 0.2 and 0.3 \AA~more distant. (wording confused Matt)
-  This behavior is not surprising since GAFF models atoms as point charges and
-  does not appropriately model the aromatic $\pi-\pi$ interactions, which would make
-  it more energetically favorable for the monomers to stack closer together ~\cite{wang_development_2004}.
-  It is also possible that the tails prevent close stacking of monomer head groups
-  and we do not achieve the timescales necessary for them to rearrange into a
-  necessarily more tightly packed configuration. To test the this chain-packing hypotheses, 
-  we equilibrated the system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
+  R-$\pi$ appears at a lower $q_z$ value in our simulations versus experiment
+  because monomers in the simulated system stack further apart than those in the
+  experimental system (Table~\ref{table:correlation_length}). We calculated
+  $z$-direction pair distribution functions, $g(z)$, as described in
+  Section~\ref{section:correlation_length}.  The resulting distributions are
+  generally characterized by decaying oscillatory behavior where the average
+  distance between peaks corresponds to the average distance between stacked
+  monomer head groups (Figure~\ref{fig:correlation}).  We calculated this
+  equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between monomers
+  using Equation~\ref{eqn:decaying_sinusoid}. The distance between stacked
+  monomers is greater than experiment by 0.5--0.9 \AA~across all cases, with
+  disordered basins at the high end of that range. This behavior is not
+  surprising since GAFF models atoms as point charges and does not appropriately
+  model the aromatic $\pi-\pi$ interactions, which would make it more
+  energetically favorable for the monomers to stack closer together
+  \cite{wang_development_2004}. It is also possible that the tails prevent
+  close stacking of monomer head groups and we do not achieve the timescales
+  necessary for them to rearrange into a necessarily more tightly packed
+  configuration. To test this chain-packing hypotheses, we equilibrated the
+  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
   into a more tightly packed configuration. Before annealing and in order to
   stabilize the hexagonal phase at 500 K, we placed harmonic restraints with
-  force constants of 1000 kJ mol$^{-1}$ nm$^{-2}$ between head group COMs
-  within each column as well as between head group COMs in
-  adjacent columns. We saw no improvement in packing distance over our 300 K
-  models (see further discussion in Section~\ref{section:slow_dynamics}).
+  force constants of 1000 kJ mol$^{-1}$ nm$^{-2}$ between head group COMs within
+  each column as well as between head group COMs in adjacent columns. We saw no
+  improvement in packing distance over our 300 K models (see further discussion
+  in Section~\ref{section:slow_dynamics}).
 
@@
   \caption{1D correlation functions of the center of masses of aromatic head
-	  groups, $g(z)$, show decaying oscillatory behavior and have consistent correlation lengths with experiment. We calculated the
-	  correlation length by fitting a decaying exponential function
+	  groups, $g(z)$, show decaying oscillatory behavior and have consistent
+	  correlation lengths with experiment. We calculated the correlation length by
+	  fitting a decaying exponential function
 	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
@@
 	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
-	  correlation length for (d) because there are no clear peaks. We assume that this
-	  correlation length is less than the vertical distance between monomers.}\label{fig:correlation}
+	  correlation length for (d) because there are no clear peaks. We assume that
+	  this correlation length is less than the vertical distance between
+	  monomers.}\label{fig:correlation}
   \end{figure}
@@
   \end{tabular}
-  \caption{The correlation length is larger for systems in the ordered basin. The equilibrated vertical
-  stacking distance, $\mathit{d}_{equil}$, is also smaller.}
+  \caption{The correlation length is larger for systems in the ordered basin.
+	  The equilibrated vertical stacking distance, $\mathit{d}_{equil}$, is also
+	  smaller.}
   \label{table:correlation_length}
@@
   positions (thermal disorder) as well as their idealized positions (quenched disorder) to use 
-  as simulated disorder into our model system.}
+  as simulated disorder in our model system.}
   \label{table:quenched_disorder} 
@@
   the simulated diffraction patterns smooths out. We can demostrate this by
-  creating a simplified sandwiched configuration (as described above), 
-  with varying amounts of statistical correlation between columns 
-  (see Figure~\ref{fig:column_displacement}). In the low independent motion limit
-  limit, the COM of columns are situated at the same $z$-coordinate.
-  We allow increasing independence of columns by randomly shifting each column in
-  the $z$-direction according to a uniform distribution bounded by (0, $f \times
-  \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We limit this discussion
-  to the sandwiched configuration since it is not feasible for columns in the
-  parallel displaced configuration, as we have set them up, to move past each
-  other. When $f = 1$, the columns move independently and the $q_r$ cross-section
-  smooths out completely (Figure~\ref{fig:sf_qy_sr100}). Any amount of
-  dependence results in some presence of independent sharp peaks, though
-  significantly attenuated at $f$ nearer 1. The intensity of R-$\pi$ also
-  decreases with increasing column independence. We see an 8-fold decrease in the
-  intensity of R-$\pi$ when $f=1$ versus when $f=0$ for our simplified model
-  systems.
+  creating a simplified sandwiched configuration (as described above), with
+  varying amounts of statistical correlation between columns (see
+  Figure~\ref{fig:column_displacement}). In the low independent motion limit, the
+  COM of columns are situated at the same $z$-coordinate.  We allow increasing
+  independence of columns by randomly shifting each column in the $z$-direction
+  according to a uniform distribution bounded by (0, $f \times \mathit{d}$) where
+  $f$ ranges between 0 and 1 and $d$ is the vertical distance between scatterers.
+  %BJC: removed this sentence since I do parallel displaced config in the ensemble
+  %We limit this discussion to the sandwiched configuration since it is not
+  %feasible for columns in the parallel displaced configuration, as we have set
+  %them up, to move past each other. 
+  When $f = 1$, the columns move independently and the $q_r$ cross-section
+  smooths out completely (Figure~\ref{fig:sf_qy_sr100}). Any amount of dependence
+  results in some presence of sharp peaks, though significantly attenuated at $f$
+  nearer 1. The intensity of R-$\pi$ also decreases with increasing column
+  independence. We see an 9-fold decrease in the intensity of R-$\pi$ when $f=1$
+  versus when $f=0$ for our simplified model systems.
 
@@
 	  amount of independence, $f$ = 0.75, the intensity of R-$\pi$ decreases 5-fold
-	  to 3.7. The edges of the peak are beginning to smooth out, but sharp peaks
+	  to 3.4. The edges of the peak are beginning to smooth out, but sharp peaks
 	  still exist. (c) When columns are completely independent, $f$ = 1, the
-	  intensity of R-$\pi$ decreases 8-fold to 2.3 and the cross-section is
+	  intensity of R-$\pi$ decreases 9-fold to 2.1 and the cross-section is
           relatively smooth.}\label{fig:column_displacement}
@@
   $z$-slices in $g(z)$ for our system, rather than restricting it to those 
-  $z$-slices within 2.1~\AA of the center of the correlation function 
+  $z$-slices within 2.1~\AA~of the center of the correlation function 
   (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
@@
   \caption{When we average all $z$-slices of the 3D correlation function, the 
-  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
+  correlation length of the ordered sandwich configuration nearly triples compared 
+  %BJC: added figure reference below. Check that it works
+  to that shown in Figure~\ref{fig:z_correlation_sandwich}.}\label{fig:z_correlation_fullbox}
   \end{figure}
@@
   \end{subfigure}
-  \caption{The $q_r$ section of R-$\pi$ is much smoother than~\ref{fig:sim_rsection_fit} when
+  \caption{The $q_r$ section of R-$\pi$ is much smoother than Figure~\ref{fig:sim_rsection_fit} when
   		   we generate simulated XRD patterns from an ensemble of 40 independent simulations,
@@
   R-double does not appear in any of the simulated diffraction patterns
-  generated using the systems simulated up to this point. Here we hypothesize a
+  generated using the systems simulated up to this point. Here we hypothesize 
   several configurational arrangements which may lead to the appearance of R-double and
@@
   result in the appearance of R-double below, and we can speculate which makes
-  the most physical sense. It appears that we cannot achieve a long-term stable
-  system that exhibits R-double without the inclusion of small amounts of water
-  in the pores.
+  the most physical sense. 
+  %BJC: seems redundant from last sentence of above paragraph
+%It appears that we cannot achieve a long-term stable
+%  system that exhibits R-double without the inclusion of small amounts of water
+%  in the pores.
 
@@
   The addition of water to the system promotes the appearance of R-double, providing
-  an answer to question~\ref{point:water} posed in the introduction.
+  an answer to Question~\ref{point:water} posed in the introduction.
   We added water to the parallel displaced and sandwiched configurations in the
@@
 	  adjacent monomers (top), R-double is visible while the heavy atoms of the head
-	  groups are held in place with position restraints (middle). Again, R-double
+	  groups are held in place with position restraints (middle). R-double
 	  fades once the position restraints are released. (b) When monomers are
@@
   a separation process. We aim to further understand the pore architecture, in
-  order to address Question~\ref{point:composition} posted in the introduction, 
+  order to address Question~\ref{point:composition} posed in the Introduction, 
   and observe the differences, if any, between the different plausible equilibrated
@@
 
-  Experimentally, membranes are cross-linked for mechanical stability before use. We applied 
-  our cross-linking algorithm to equilibrated sandwiched and parallel
-  displaced configurations in the ordered pore basin. We allowed the cross-linking
-  algorithm to propagate until greater than 90\% of the vinyl groups on the tails of the 
-  monomers were either involved in a cross-linking reaction or were terminated 
-  (see Section \ref{S-section:xlink} of the SI)
-  for further details of the cross-linking algorithm). We allowed the cross-linked
+  Experimentally, membranes are cross-linked for mechanical stability before
+  use. We applied our cross-linking algorithm to equilibrated sandwiched and
+  parallel displaced configurations in the ordered pore basin. We allowed the
+  cross-linking algorithm to propagate until greater than 90\% of the vinyl
+  groups on the tails of the monomers were either involved in a cross-linking
+  reaction or were terminated (see Section \ref{S-section:xlink} of the SI for
+  further details of the cross-linking algorithm). We allowed the cross-linked
   configurations to simulate for 100 ns further in the NPT ensemble.
@@
   exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)
-  configuration remains constant. The pore spacing of both systems decreases upon crosslinking.
+  configuration remains constant. The pore spacing of both systems decreases upon cross-linking.
   The vertical distance between stacked monomers increases in the sandwiched configuration
@@
   predicted. We find that R-spots is likely due to ordered alkane chain packing.
-  R-$\pi$ appears at lower q values than experiment because monomer stack too far
+  R-$\pi$ appears at lower $q_z$ values than experiment because monomer stack too far
   apart, and its intensity is far too high, likely because our initial
@@
 
-  Molecular simulations were performed using the Extreme Science and Engineering Discovery
-  Environment (XSEDE), which is supported by National Science Foundation grant number 
-  ACI-1548562. Specifically, it used the Bridges system, which is supported by NSF award
-  number ACI-1445606, at the Pittsburgh Supercomputing Center (PSC). Simulations were also
-  performed on Summit super computer, which is supported by the NSF grant OAC-1532235. 
-  This work was supported financially by NSF through the grant NSF-CBET 1351635.
+  Molecular simulations were performed using the Extreme Science and
+  Engineering Discovery Environment (XSEDE), which is supported by National
+  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
+  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
+  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
+  which is supported by the National Science Foundation (awards ACI-1532235 and
+  ACI-1532236), the University of Colorado Boulder, and Colorado State
+  University. The Summit supercomputer is a joint effort of the University of
+  Colorado Boulder and Colorado State University.
 
@@
   \begin{figure}
-  \includegraphics[width=4.5cm]{toc_image_final.pdf}
-  \includegraphics[width=4.07cm]{toc_waxs.pdf}
+  \includegraphics[width=3.5in]{new_toc_graphic.pdf}
+%  \includegraphics[width=4.5cm]{toc_image_final.pdf}
+%  \includegraphics[width=4.07cm]{toc_waxs.pdf}
  \end{figure}

### 2018-10-11 Ben_Manuscripts/structure_paper/supporting_information.tex
Updated drafts.
Final read-through edits

@@
   (.trr or .xtc) and a configuration file (.gro), simulate an XRD pattern using
-  \texttt{main\_gromacs.py}. Pass the flag \texttt{\-manuscript\_format} to generate patterns
+  \texttt{main\_gromacs.py}. Pass the flag \texttt{\--manuscript\_format} to generate patterns
   and cross-sections with the same format as those presented in the main text.
@@
 	output of \texttt{antechamber} to create Amber topology files. A detailed
-	tutorial for using \texttt{LEaP} for parameterizationcan be accessed elsewhere \cite{walker_antechamber_nodate}.
+	tutorial for using \texttt{LEaP} for parameterization can be accessed elsewhere \cite{walker_antechamber_nodate}.
 
@@
 	\end{subfigure}
-	\caption{(a) In a perfect hexagonal, there are 5 distances that should be exactly
+	\caption{(a) In a perfect hexagonal array, there are 5 distances that should be exactly
 	equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
@@
   \caption{When creating an initial configuration, we define the pore radius,
-  $\mathbf{R}$, based on the distance of the carbonyl carbon from the pore's
+  R, based on the distance of the carbonyl carbon from the pore's
   central axis.}~\label{fig:pore_radius_illustration}
@@
 	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
-	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
+	Equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
 	spacings.
@@
   box vectors, however this technique does not fully capture the uncertainty
-  in the individual pore-to-pore distances.
+  in the individual pore-to-pore distances (Table~\ref{table:p2p}).
 
@@
   \section{Component radial density functions}\label{section:radial_density}
-
+ %BJC: can probably delete this figure 
   \begin{figure}[!htb]
@@
 	  composition gradient transitioning from the hydrophilic to the hydrophobic
-	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
+	  regions. Systems with monomers initially stacked 3.7 \AA~apart in the parallel
 	  displaced (a), and sandwiched (b) configurations both show the highest
@@
   \caption{
-  Looking down onto the plane of membrane, 
+  Looking down onto the $xy$ plane of the membrane, 
   % this diagram
@@
   \section{Ionic Conductivity}\label{section:ionic_conductivity}
-
+ %BJC: add plot of collective diffusion values 
   In the main text, we calculated ionic conductivity using the Nernst-Einstein
-  relationship. We also measured ionic conductivity using a second method, 
-  termed the collective diffusion model\cite{liu_collective_2013}, for robustness. The collective 
-  diffusion model measures the movement of the collective variable, Q, which
-  is defined as the amount of charge transfer through the system and can be 
-  thought to represent the center of charge of the system. The conductance, 
-  $\gamma$, of the system can be calculated as:
+  relationship. We also measured ionic conductivity using a second method, termed
+  the collective diffusion model\cite{liu_collective_2013}, for robustness
+  (Figure~\ref{fig:conductivity}). The collective diffusion model measures the
+  movement of the collective variable, Q, which is defined as the amount of
+  charge transfer through the system and can be thought to represent the center
+  of charge of the system. The conductance, $\gamma$, of the system can be
+  calculated as:
   \begin{equation}
@@
   Systems in the ordered basin have higher nematic order parameters than their
-  disordered basin counterparts. Both sandwiched system have higher nematic order
+  disordered basin counterparts. Both sandwiched systems have higher nematic order
   parameters than both parallel displaced systems. This may occur because monomers
@@
   Monomer tails prefer to lie flat rather than tilt with respect to the
-  membrane plane. We created a monomer whose tails tilted ca. 30$\degree$. 
-  We added position restraints to the ends of the monomer tails with the
-  same force constant as the head groups (see section~\ref{section:equilibration}).
-  As we slowly reduce the force constants, the tails begin to tend towards
-  a negligible tilt angle (Figure~\ref{fig:tail_tilt}).
-
-  \begin{figure}[!htb]
-  \centering
-  % seems to be missing in the repository? tilt_cat.png
+  membrane plane. We created a monomer whose tails tilt ca. 30$\degree$ with
+  respect to the $xy$ membrane plane.  We added position restraints to the ends
+  of the monomer tails with the same force constant as the head groups (see
+  section~\ref{section:equilibration}).  As we slowly reduce the force constants,
+  the tails begin to tend towards a negligible tilt angle
+  (Figure~\ref{fig:tail_tilt}).
+
+  \begin{figure}[!htb]
+  \centering
+  %MRSF2: seems to be missing in the repository? tilt_cat.png
   \includegraphics[width=0.5\textwidth]{tilt_cat.png}
@@
   \centering
+  %MRSF2: figure missing in repository. 
   \includegraphics[width=0.5\textwidth]{carboxylate_dihedrals.pdf}
@@
   The appearance of R-double is likely a consequence of structure induced when
-  vertically stacked monomer pairs share hydrogen bonds with a common water molecules (See
+  vertically stacked monomer pairs share hydrogen bonds with a common water molecule (See
   Section~\ref{M-section:rdouble} of the main text). We quantified the occurence of
@@
   (Figure~\ref{fig:pore_hbonds_ft}). We see the strongest indicator of asymmetric monomer
-  stacking in Pore 1 where the peaks at 0.75 $\AA^{-1}$ are clearly distinguishable, meaning
+  stacking in Pore 1 where the peaks at 0.76 $\AA^{-1}$ are clearly distinguishable, meaning
   there is periodicity at twice the $\pi$-stacking distance.

### 2018-10-11 Ben_Manuscripts/structure_paper/Final_Draft.tex
New toc graphic

@@
   More highly selective nanoporous membranes would be extremely useful for
-% BJC: in --> for
   performing complex aqueous separations with seawater and various types of
@@
   research area for aqueous separation applications because they offer the
-  %BJC: separations --> separation 
   ability to control pore architecture at the molecular scale, thereby
@@
 	create columns with short range order, then assemble into pores with 
-        %BJC: order --> order, (added comma) 
 	hydrophilic head groups (blue) facing towards the pore center. (e) The 
@@
 
-  In this study, we achieve a more realistic atomistic description of a
-  %BJC: of --> of a
+  In this study, we achieve a more realistic atomistic description of
   hexagonal LLC polymer membranes than, to our knowledge, has ever previously
@@
 	location of all spots is $\sim37^{\circ}$ from the $q_r$ axis in their
-	%BJC: q_z --> q_r
 	respective quadrants. In many liquid crystal systems, such spots are explained
@@
   that a united-atom model of an LLC can self-assemble into the
-  %BJC: show a united-atom --> that a united-atom ; of LLC --> of an LLC
   H\textsubscript{II} phase configuration in $\sim$1000 ns
@@
   the slow self-assembly process, we used automated procedures to
-  %BJC: a variety of automated --> automated
   assemble monomers into a structure close to one of a number of hypothesized
@@
   that is largely locked into place for the remainder of the simulation, even at
-  %BJC: and --> that
   the 100 ns time scale. We measured thermal disorder by calculating the standard
@@
   pore-to-pore distances within error, but stack too far apart. 6
-  %BJC: Monomers in 6 --> 6
   column per pore disordered sandwiched and disordered parallel displaced
@@
   $f$ ranges between 0 and 1 and $d$ is the vertical distance between scatterers.
-  %BJC: removed this sentence since I do parallel displaced config in the ensemble
-  %We limit this discussion to the sandwiched configuration since it is not
-  %feasible for columns in the parallel displaced configuration, as we have set
-  %them up, to move past each other. 
   When $f = 1$, the columns move independently and the $q_r$ cross-section
@@
   correlation length of the ordered sandwich configuration nearly triples compared 
-  %BJC: added figure reference below. Check that it works
   to that shown in Figure~\ref{fig:z_correlation_sandwich}.}\label{fig:z_correlation_fullbox}
@@
   the most physical sense.
-  %BJC: seems redundant from last sentence of above paragraph
-%It appears that we cannot achieve a long-term stable
-%  system that exhibits R-double without the inclusion of small amounts of water
-%  in the pores.
 

### 2018-10-23 Ben_Manuscripts/structure_paper/figures/bridges_achievement.tex

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{figure}
\includegraphics[width=\textwidth]{toc_image_final.pdf}
\caption*{We studied the atomistic structure of a lyotropic liquid crystal
	(LLC) membrane using molecular dynamics simulations run for hundreds of
	nanoseconds enabled by Bridges GPU nodes. We learned that the membrane pores
	(represented by blue sodium ions and yellow LLC monomer head groups above) are
	dense with a gradual transition from hydrophilic to hydrophobic character as
	distance from the pore center increases. We will use our model, which has been
	validated with experimental studies, in order to characterize transport of
	small molecules inside the nanopores so we can learn how to design new LLC
	membranes for solute-specific separations.} 
\end{figure}

\end{document}

### 2018-11-13 Ben_Manuscripts/Masters_Bypass/conclusion.tex
edits

@@
-\section{Conclusion}
+\section*{Conclusion}
 
@@
 Basin B has not been seen experimentally. We hypothesize that Basin B will
-be dominant at higher temperatures. This hypothesis will be tested in future 
-work. In addition to structural accuracy, our model's physical properties
-are consistent with experimental measurements. Ionic conductivity, calculated
-in two ways, is in reasonable agreement with experiment. The procedure used
-to create and validate our model can be used to evaluate other liquid 
-crystalline assemblies. Using the design framework and analysis methods 
-applied herin, we have the ability to understand structures of new and
-unsynthesized nanoporous membranes.
+be dominant at higher temperatures. Our model's inability to capture aromatic
+interactions likely destabilizes Basin A at room temperature and enhances 
+the stability of Basin B. Basin B is likely a part of the transition towards
+the isotropic phase which exists at high temperatures. This hypothesis will
+be tested in future work. In addition to structural accuracy, our model's
+physical properties are consistent with experimental measurements. Ionic
+conductivity, calculated
+in two ways, is in reasonable agreement with experiment. Using the design
+framework and analysis methods applied herin, we have the ability to 
+understand structures of new and unsynthesized LLC membranes.

### 2018-11-13 Ben_Manuscripts/Masters_Bypass/intro.tex

@@
 A molecular level understanding of LLC membrane structure will elucidate
-small molecule transport mechanisms, providing guidelines for reducing the
+small molecule transport mechanisms, providing guidelines to reduce the
 chemical space for the design of monomers used to create separation-specific
@@
 size or how to tune the chemical environment in the 
-nanopores for effective water desalination and small organic separations.
+nanopores for effective water desalination or small organic separations.
 Rejection studies show that this membrane can not perform separations of solutes less than 1.2 nm  
@@
 % Thesis 1
-A clear picture of the nanoscopic structure of LLC membranes, gained by
-building a molecular model will provide evidence to support or call
-into question past drawn conclusions that have largely guided our 
-understanding of the system. 
+% A clear picture of the nanoscopic structure of LLC membranes, gained by
+% building a molecular model will provide evidence to support or call
+% into question past drawn conclusions that have largely guided our 
+% understanding of the system. 
 % Thesis 2
@@
 are seven monomers in each layer~\cite{resel_structural_2000}. 
-Once we %BJC: why is knowing the number of monomers in each layer important to experimentalists at all - find monomers which prefer to pack more densely - high ionic conductivity?
-know the number of monomers in each layer, we still do not know how 
+A molecular model has the best chance of directly answering this question.
+Once we know the number of monomers in each layer, we still do not know how 
 monomers in each layer are positioned with respect to other layers. 
@@
 interested in reproducing the conclusions about structure which have been
-made from XRD experiments and ionic conductivity measurements
+made from X-ray diffraction (XRD) experiments and in matching ionic conductivity measurements
 \cite{feng_thin_2016}. We have comparied simulated X-ray diffraction
 patterns to experiment in order to match major features present in the
-2D patterns. We calculate ionic conductivity using two agreeing methods.
+2D patterns. We calculated ionic conductivity using two agreeing methods.
 We examined the the influence of crosslinking on membrane structure. 

### 2018-11-13 Ben_Manuscripts/XSEDE/bridges_2017/progress.tex

@@
 Additionally, we were able to explain the spots that appear (red arrows
-in figure xx) contrary to how it was originally reported. The spots 
+in Fig.~\ref{metastable}) contrary to how it was originally reported. The spots 
 were assumed to be caused by the 40 degree tilt angle of the alkyl
@@
 will be submitted in the coming months. In the future, we will conduct
-free energy calculations that will help explain the difference between
+free energy calculations that will quantify the relative stability of
 the two states and and help predict what experimental conditions might
-lead to each.
+lead to each. We will also explore transport properties in each 
+configuration to see which state provides optimal performance.
 
@@
 non-trivial. We do not know exactly the equilibrium content of water 
-or where the water is situated. While it is clear that most water should be in the hydrophilic pore region, simulations have shown that an 
+or where the water is situated in the membrane. While it is clear that 
+most water should be in the hydrophilic pore region, simulations have shown that an 
 appreciable amount of water can exist in the tail region near the 
 slightly hydrophilic ester group. The best way to figure out how much 
-water should be in the pore is to run very long equilibration simulationsand allow the simulations to tell us. Our current approach is to create
+water should be in the pore is to run very long equilibration simulations
+and allow the simulations to tell us. Our current approach is to create
 water baths at each face of the membrane and allow water to diffuse into
@@
 water in 1000 nanoseconds. Studies of the hydrated, 'lyotropic', phase
-will be the subject of a subsequent publication.
+will be the subject of a future publication.

### 2018-11-13 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex

@@
   \caption{(a) The intensity of R-$\pi$ decays to 1 rapidly as gaussian noise is 
-   added to the system. (b) When we add noise in the x and y directions, R-$\pi$
+   added to the system in the z-direction. (b) When we add noise in the x and y directions, R-$\pi$
    broaden in the y-direction with a continuous intensity distribution that can be
@@
   \end{subfigure}
-  \caption{}\label{fig:com_distribution}
+  \caption{(a) Distribution of xy center of mass positions of monomer head groups from
+  the pore center. (b) Distribution of z center of mass positions of monomer head 
+  groups from idealized 'layer' locations.}\label{fig:com_distribution}
   \end{figure}

### 2018-11-13 Ben_Manuscripts/structure_paper/Draft.tex

@@
 
-  % BJC5: Note to self -- how to use latex xr : Figure S~\ref{S-fig:monomer_color_coded}
+  % Note to self -- how to use latex xr : Figure S~\ref{S-fig:monomer_color_coded}
 
   More highly selective nanoporous membranes would be extremely useful 
-  %in order to perform 
   in performing complex aqueous separations with seawater and various 
-  %sources 
-  types of
-  wastewater. 
-  For exaple, 
-  Sodium chloride and boron in seawater
+  types of wastewater. For example, Sodium chloride and boron in seawater
   \cite{fritzmann_state---art_2007} and organic micropollutants found in
-  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} represent just a few of the diverse contaminants 
-  of water sources. By efficiently
+  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} represent
+  just a few of the diverse contaminants of water sources. By efficiently
   separating contaminants from feed solutions with highly selective membranes,

### 2018-11-15 Ben_Manuscripts/structure_paper/response_to_reviewers.tex
Response to reviewers

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}

\title{Response to reviewers: Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author{Benjamin J. Coscia \and Joseph Yelk \and Matthew A. Glaser \and Douglas L. Gin \and Xunda Feng \and Michael R. Shirts}

\begin{document}

\maketitle

We thank the reviewers for carefully reading over our manuscript and providing helpful comments. We have taken the suggestions into consideration and made appropriate revisions to the manuscript document. All changes to the text have been documented below.

\section{Response to Reviewer 1}

\begin{enumerate}

	\item \begin{quote} \textit{This manuscript describes atomistic molecular dynamics simulations and
	diffraction analysis of hexagonally-arranged pores, each of which is made of many columns of the 
	monomer Na-GA3C11. This physical system is of interest because such nanopores have potential to 
	transform filtration applications. This work is of potential interest to the JPC readership because
	it provides atomistic insight into the origins of diffraction reflections observed in experiments, 
	which could be used to resolve discrepancies about what the structure of these hexagonal arrays are,
	or used to engineer better filters. Overall, the manuscript provides comprehensive descriptions of
	metrics used to evaluate the simulated structures against experiments, but the number of things
	described and length of these descriptions obscures whether significant new physical insight into
	this system is made.} \end{quote}

	Author reply: We thank the reviewer for their constructive feedback and aim to address all of their concerns.

	\item \begin{quote}
	\textit{As written, it is not clear if the authors are presenting this study as a validation of 
	GAFF and the present equilibration techniques, or whether this study is providing significant new
	physical insight into these lyotropic liquid crystals. The paper reads a bit more like the former,
	with a comprehensive discussion of the degree to which five scattering features expected in 
	experiments are predicted in simulations. However, at the same time, the authors make arguments
	including (1) pores are made from five columns of monomers, (2) that water is present in the "dry"
	structures, and (3) that a scattering feature comes from tail packing, not tilt: These observations
	*could* be new physical insight into lyotropic liquid crystal structure, but as presented seem more
	like hypotheses than conclusions:}

	%BJC: want to convery that we want to reproduce all of the experimental features as best as possible
	% using an out-of-the-box force field. That way we know we are approximating the chemical environment
	% as close to the experimental system as possible. The goal is to eventually test large numbers of 
	% monomers without the needing to dive into the excruciating detail shown here.

	\end{quote}

	\item \begin{quote}
    \textit{1. For the simulations performed here, the authors do make a strong case that 5 columns per
    core gets the best pore-to-pore spacing (Figure 5). However, insufficient time is accessed to see 
    whether the 4-, 5-, and 6-column initial conditions move towards or away from the expected pore 
    spacing over many-microseconds trajectories. That said, for the quenches performed here, 5-columns
    per core seems more plausible than 4. Is this significant physical insight? It is insight, but the
    authors do not make a compelling case for how 5 columns would change how we think about these crystals,
    or how it would impact membrane engineering (or more importantly, whether these 5-column structures
    assemble in the solution phase, or are only locally stable).}

    %BJC: can't access microseconds with simulations. Pore spacing appears stable. In order to pack monomers
    % 3.7 angstroms apart vertically, can't have 6 columns per pore. The pore spacing is always too small with 4.
    % Physical insight: Density of functional groups that interact with solutes

    \end{quote}

    \item \begin{quote}
    \textit{2. The authors make a pretty compelling case that water causes the R-double scattering feature
    by showing its absence when water is added, but that the R-double appears and persists for 200ns after
    the water makes its way into the crystal. However, the authors also show that nonuniformly spaced
    monomers can give rise to the R-Double feature, a seeming counterexample to the necessity of water.
    Is the R-double feature with water because the monomers are now irregularly spaced? What happens when
    the waters are removed and the scattering re-performed in Fig 17c(bottom)?}
    \end{quote}

    Author reply: The reviewer makes good points about R-double that need to be clarified in the main text.
    R-double appears in a dry system with non-uniformly spaced monomers. However, such a system is only 
    stable, as we've modeled it, if $z$-direction position restraints are applied to monomer head groups. As
    soon as the restraints are released, R-double fades and the monomer spacing becomes uniform. We believe 
    that water facilitates the appearance of R-double by stabilizing non-uniform spacing through hydrogen bonding,
    as the reviewer suggests. We re-performed the scattering analysis on the same system with water molecules
    removed, as suggested, and R-double is still present.

    % BJC: mention that this plot is added to supporting info and that the "head group removed" figure further
    % supports this conclusion.

	\item \begin{quote}
    \textit{3. The authors make the case that the R-spots feature comes from the structure of the hexagonal
    tails, not their tilt. The authors should perform the scattering analysis to check if the R-spots are
    present on the tilted-tails they constrain: This quick experiment would nail down their interpretation
    here, or show that the tilted tails are also plausible (but not observed in this model).}
    \end{quote}

    \item \begin{quote}
    \textit{These arguments would be stronger if there weren't so many qualifications about simulation 
    timescales and GAFF, in particular its ability to predict the shortest-scale feature (pi-stacking) for 
    this system. How does everything else change if the force-field were tuned to get that feature correct?}
    \end{quote}

	\item \begin{quote}
    \textit{The MD-Structure-Factor repository is not available at the provided github link, nor does it appear
    to be online anywhere. So, the correctness of that code cannot be checked.}
	\end{quote}

	Author reply: We thank the reviewer for pointing this out and apologize for this mistake. The referenced
	GitHub repository was set to private by our collaborators but has now been made public. Please feel 
	free to read through the code.

    \item \begin{quote}
    \textit{One might want to check that code based on Figure 7f, where presumably spherical scatterers 
    generate reflections with anisotropy (diamonds instead of squares or circles). This kind of an artefact
    is plausible if there are errors handling the non-cubic box, or with scattering angles that aren't parallel
    to a box axis. llcsim/analysis/correlation.py looks like it has the machinery for doing the scattering analysis.}
	\end{quote}

	Author reply: We thank the reviewer for their astute observation and the resulting improvements to 
	our manuscript.	We generated Figure 7f by calculating the structure factor of a 2-dimensional array of 
	hexagonally-packed scatterers. It is meant to be a simplified representation of the scattering exhibited
	by hexagonally packed alkane tails so that we can qualitatively understand where we would expect R-spots to appear if 
	tails indeed pack in that way. Since it is possible to generate a rectangular unit cell which contains 
	hexagonally packed point scatterers, there are no artifacts due to improper treatment of periodicity. 
	Although we believe our calculations are correct, we originally used only eight total scatterers in the 
	2D unit cell and then plotted the structure factor with a contour plot (\texttt{matplotlib.pyplot.contourf})
	which does not interpolate the data. We re-created Figure 7f by simulating the structure factor of 100 
	hexagonally packed scatterers, in order to get higher fourier space resolution, and then plotting the
	result with \texttt{matplotlib.pyplot.imshow} and Gaussian interpolation. We have added the code used to
	generate this figure to the \texttt{llcsim} repository which can be accessed at 
	\texttt{https://github.com/bencoscia/llcsim/blob/master/analysis/hexagonal\_packing.py}.

	% Add code and clarify main text

	\item \begin{quote}	
    \textit{Regarding the ion conductivities, how do the numbers presented here compare against ion conductivities
    predicted with GAFF and other polarizable and nonpolarizable force fields? If GAFF is systematically too high
    in other cases, it could help explain the order-of-magnitude discrepancy observed here.}
    \end{quote}

	\item \begin{quote}
    \textit{If the authors either (a) strengthen the cases for their proposed structural insights being  highly 
    likely (not just plausible), or (b) make a stronger case for why these particular insights have important 
    ramifications for our understanding of LLC's (their significance), then it would be easier to publish this 
    immediately. This reviewer's opinion is that this work would find a broader interested audience with a more
    concise focus on these physical insights, which could be accomplished by moving more content 
    (e.g., dihedral correlations) to the SI.}
    \end{quote}

\end{enumerate}

\section{Response to Reviewer 2}

\begin{enumerate}

	\item \begin{quote} \textit{The authors report a computer simulation study of the detailed structure
	of several systems, which are similar to the cross-linked inverted hexagonal phase of self-assembled
	lyotropic liquid crystals (LLCs) used to develop porous polymer membranes for separations. Specifically,
	the authors studied the Col-h thermotropic (solvent-free) phase formed by the assembly of the Na-GA3C11
	monomer, which is similar to the LLC phases used in the development of polymeric membranes. The Col-h 
	phase has been characterized experimentally using wide-angle X-ray scattering (WAXS), but nonetheless 
	important gaps in its structure still remains. Using all-atom classical molecular dynamics simulations,
	the authors performed a very careful and very detailed study of the structure of the Col-h phase formed
	by Na-GA3C11. The authors compared their simulated X-ray diffraction (XRD) patterns with existing 2D-WAXS
	experimental data, carefully discussed and explained the observed differences between simulations and 
	experiments, and provided molecular-level details of the structure of this system that cannot be obtained
	from experiments. This study is very detailed; all relevant information is provided for interested readers
	to replicate results from this study (including links to Python scripts used to set up the simulations, 
	analyze MD trajectories, and obtain simulated XRD patterns). The simulation results has been analyzed and
	discussed comprehensively (perhaps too comprehensively, as this paper is 63 pages long, has 21 figures and
	its Supporting Information file has 19 additional pages; however, I don’t think the authors should make any
	efforts to shorten the paper, as I feel every presented component is required to fully understand the 
	contributions of this study) Overall this is an extremely solid manuscript}\end{quote}

	Author reply: We thank the reviewer for the kind assessment of our work. We also acknowledge that this is a long article

	\item \begin{quote}

	\textit{I have no suggestions to further improve this paper, other than fixing a few small typos:}

    \textit{(1) Page 10, first paragraph: remove the ‘page 58’ associated with reference 25}

    \textit{(2) Page 54: reference to the paper of Feng et al is missing}

	\end{quote}

    Author reply: We thank the reviewer for pointing out these minor errors in our main text. These issues have been corrected in
    the revised main text file. % need to add page numbers once finished

    \item \begin{quote} \textit{(3) Page 54: mention examples of force fields that explicitly include pi-pi interactions
    } \end{quote}

    Author reply: We have adjusted our language in order to specifically mention and cite polarizable force fields as follows:

    ``Polarizable force fields explicitly including $\pi-\pi$ interactions may be able to draw stacked
    monomers closer together"

\end{enumerate}

\end{document}

### 2018-11-15 Ben_Manuscripts/structure_paper/Final_Draft.tex
Response to reviewers

@@
 
-  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:assembly}) has a
+  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:hex_packing_simple}) has a
   higher theoretical capacity for transport than the Q\textsubscript{I} phase.
@@
   MD simulations can provide the required level of detail (Figure
-  \ref{fig:detail}), assuming the force fields are sufficiently accurate.  With
+  \ref{fig:detailed_pore}), assuming the force fields are sufficiently accurate.  With
   such an atomistic model, we can directly observe molecular-level solute
@@
 	crystalline systems have long range order in 1 or 2 spatial dimensions and
-	short range order in the other dimensions.~\cite{chaikin_principles_1995}  %
-	page 58 In the system we are studying, there are long-range 2D correlations in
+	short range order in the other dimensions.~\cite{chaikin_principles_1995}  % page 58
+	In the system we are studying, there are long-range 2D correlations in
 	the hexagonal array of pores ($xy$ plane) and short range $z$-direction
@@
   pattern, R-$\pi$, as it appears in the simulated diffraction patterns,
-  intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set an upper bound
+  intersects with R-alkanes (See Section~\ref{section:rpi}). We set an upper bound
   on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$.  Intensities
@@
   average distance between stacked monomers, and an amplitude that decays exponentially
-  (see Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
+  (see Section~\ref{section:rpi}). The rate of decay is related to the correlation 
   length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$,
@@
 		Parallel displaced, disordered basin configurations with (c) experimental WAXS.
-		The major reflections of interest (See Figure~\ref{fig:SWAXS} for their
+		The major reflections of interest (See Figure~\ref{fig:WAXS} for their
 		definitions) are present at varying degrees. In all cases, R-pores, R-alkanes
@@
   12\% and 27\%, we saw a 3 and 15-fold decrease in the maximum intensity of 
-  R-$\pi$ respectively (Figure~\ref{fig:znoise}). Despite the decrease in 
+  R-$\pi$ respectively (Figure~\ref{fig:intensity_vs_zsigma}). Despite the decrease in 
   intensity, the 3 cross-sections have the same shape 
@@
 
-  We plotted the number densities of heavy atoms in the head group, carbon atoms in the tail
-  region and all sodium ions (Figure~\ref{fig:overlaid_densities}). For the head group
-  region, we used heavy atoms making up the aromatic rings and carboxylate groups. For the tail
-  region, we used carbon atoms of the monomer tails (See Figure \ref{S-fig:monomer_color_coded}
+  We plotted the number densities of heavy atoms in the head group 
+  (Figure~\ref{fig:head_groups_regional_density}), carbon atoms in the tail region 
+  (Figure~\ref{fig:tails_regional_density}) and all sodium ions 
+  (Figure~\ref{fig:sodium_regional_density}). For the head group region, we used heavy
+  atoms making up the aromatic rings and carboxylate groups. For the tail region, we
+  used carbon atoms of the monomer tails (See Figure \ref{S-fig:monomer_color_coded}
   of the SI for a diagram). We averaged the histograms over the equilibrated
@@
   \begin{subfigure}{0.32\textwidth}
-        \includegraphics[width=1\linewidth]{sodium_density.pdf}
-        \caption{Sodium Ions}
-        \label{fig:sodium_regional_density}
-  \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
         \includegraphics[width=1\linewidth]{head_group_density.pdf}
@@
         \label{fig:tails_regional_density}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{sodium_density.pdf}
+        \caption{Sodium Ions}
+        \label{fig:sodium_regional_density}
   \end{subfigure}
@@
   observation has possible implications for the reproducibility of the experimental
-  results from Feng et al. since they specify that their membrane is synthesized dry.
+  results of Feng et al.~\cite{feng_scalable_2014,feng_thin_2016} since they
+  specify that their membrane is synthesized dry.
 
@@
   Future work, based on what has been learned in this study, may help further
-  improve the structural agreement between experiment and simulation. Force 
-  fields explicitly including $\pi-\pi$ interactions may be able to draw stacked
-  monomers closer together. We can study ensembles of long simulations in order
+  improve the structural agreement between experiment and simulation. 
+  Polarizable force fields explicitly including $\pi-\pi$ interactions may be
+  able to draw stacked monomers closer together 
+  ~\cite{shi_polarizable_2013,kaminski_development_2004,lopes_polarizable_2007}. 
+  We can study ensembles of long simulations in order
   to observe more averaged structure and to create more experimentally consistent
@@
 
-  \section*{Graphical TOC Entry}
+  \section*{TOC Graphic}
   \begin{figure}
-  \includegraphics[width=3.5in]{new_toc_graphic.pdf}
+  \includegraphics[width=3.25in]{new_toc_graphic.pdf}
 %  \includegraphics[width=4.5cm]{toc_image_final.pdf}

### 2018-11-15 Ben_Manuscripts/structure_paper/supporting_information.tex
Response to reviewers

@@
 \usepackage{array}
+\usepackage{authblk}
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
@@
 \renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\thepage}{S\arabic{page}}  
+\renewcommand{\thetable}{S\arabic{table}}
 
@@
 \externaldocument[M-]{Final_Draft}
+
 \title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
-\author{Benjamin J. Coscia \and Jospeh Yelk \and Matthew A. Glaser \and Douglas L. Gin \and Xunda Feng \and Michael R. Shirts}
-\date{}
+\author[1]{Benjamin J. Coscia}
+\author[2]{Joseph Yelk}
+\author[2]{Matthew A. Glaser}
+\author[1,3]{Douglas L. Gin}
+\author[4]{Xunda Feng}
+\author[1]{Michael R. Shirts*}
+\date{E-mail: michael.shirts@colorado.edu}
+
+\affil[1]{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+\affil[2]{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
+\affil[3]{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
+\affil[4]{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
 
@@
   \bibliographystyle{ieeetr}
-  \graphicspath{{./figures/}}  % put all the figures here
+  \graphicspath{{./figures/supporting_figures/}}  % put all the figures here
   \maketitle
@@
 
-  Based on evidence from section~\ref{M-section:rpi} of the main text, we
+  Based on evidence from Section~\ref{M-section:rpi} of the main text, we
   believe it is most likely that the head groups stack somewhere between
@@
   of the monomer tails with the same force constant as the head groups (see
-  section~\ref{section:equilibration}).  As we slowly reduce the force constants,
+  Section~\ref{section:equilibration}).  As we slowly reduce the force constants,
   the tails begin to tend towards a negligible tilt angle
@@
 
-  In section~\ref{M-section:slow_dynamics} of the main text, we calculated the
+  In Section~\ref{M-section:slow_dynamics} of the main text, we calculated the
   autocorrelation function of the outer tail either dihedrals pictured

### 2018-11-17 Ben_Manuscripts/structure_paper/response_to_reviewers.tex
Working on response to reviewers

@@
 \usepackage{amsmath}
+\usepackage{xr}
+
+\externaldocument[S-]{supporting_information}
+\externaldocument[M-]{Final_Draft}
 
@@
     spacing over many-microseconds trajectories. That said, for the quenches performed here, 5-columns
-    per core seems more plausible than 4. Is this significant physical insight? It is insight, but the
+    per core seems more plausible than 4.}
+	\end{quote}
+
+	Author reply: We agree with the reviewer that 5-columns per core is more plausible than 4 and that much
+    longer simulations may provide further supporting evidence. However, there is very little motion on
+    the hundreds of nanoseconds timescale which we simulated which suggests that we will not gain any 
+    significant new insight by extending our simulations into the microsecond regime. It is not feasible 
+    for us to carry out these simulations as it would consume our computational resources with little reward.
+    %BJC: The following might apply:
+    Some confusion may have been generated by agreement of the disordered basin 6 column-per-pore system
+    with experimental pore spacing. As mentioned in the text, the vertical stacking distance between monomers
+    in that system is far too large. The columns are `stretch' in the $z$-direction allowing the pores take
+    up less space on the $xy$ plane and thus pack closer together.
+
+	\item \begin{quote}    
+    \textit{Is this significant physical insight? It is insight, but the
     authors do not make a compelling case for how 5 columns would change how we think about these crystals,
@@
     assemble in the solution phase, or are only locally stable).}
+    \end{quote}
 
-    %BJC: can't access microseconds with simulations. Pore spacing appears stable. In order to pack monomers
-    % 3.7 angstroms apart vertically, can't have 6 columns per pore. The pore spacing is always too small with 4.
-    % Physical insight: Density of functional groups that interact with solutes
+    Author reply: We thank the reviewer for pushing us to provide more significant physical insight based
+    on the number of monomers per column. The number of columns-per-pore influences the pore radius which
+    is important for determining the limits of size-exclusion-based separations. It also tells use the 
+    density of interacting sites within the pore which may play a role in small molecule transport. We have
+    added the following text to the main document at the end of Section~\ref{M-section:mon_per_pore} on 
+    page _:
 
-    \end{quote}
+    ``The number of columns per pore dictates the density of interaction sites within each pore and the 
+    pore radius. A higher number of interaction sites will surely play a role in transport of molecules
+    that have an affinity for the monomer head groups. 
+    %We measured the pore radius as the average distance from the pore center to each head group COM. 
+    The pore radius increases with the number of columns per pore (See Figure~\ref{S-fig:pore_radius}. 
+    This radius is likely related to the size of the molecules which can be excluded by this type of 
+    membrane. We may be able to control LLC membrane pore size by selecting monomers that are stable
+    in configurations with more columns-per-pore."
 

### 2018-11-17 Ben_Manuscripts/structure_paper/Final_Draft.tex
Working on response to reviewers

@@
   therefore focus on the analysis of systems built with 5 columns per pore.
+
+  %BJC: added.
+  The number of columns per pore dictates the density of interaction sites within
+  each pore and the pore radius. A higher number of interaction sites will 
+  surely play a role in transport of molecules that have an affinity for the monomer
+  head groups. 
+  %We measured the pore radius as the average distance from the pore
+  %center to each head group COM. 
+  The pore radius increases with the number of 
+  columns per pore (See Figure~\ref{S-fig:pore_radius}. This radius is likely 
+  related to the size of the molecules which can be excluded by this type of 
+  membrane. We may be able to control LLC membrane pore size by selecting monomers
+  that are stable in configurations with more columns-per-pore.
 
@@
   distance between peaks corresponds to the average distance between stacked
-  monomer head groups (Figure~\ref{fig:correlation}).  We calculated this
+  monomer head groups (Figure~\ref{S-fig:correlation}). We calculated this
   equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between monomers
@@
 
+  %BJC: could move the following paragraph to supporting
   The system size, in the $z$-direction, does not significantly alter $g(z)$.
-  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
+  In Figure~\ref{S-fig:correlation}, oscillations do not fully decay, so a taller
   system may be necessary to fully capture the correlation function. We therefore
@@
 
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
-  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
-  \end{subfigure}  
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
-  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
-  \end{subfigure}  
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
-  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
-  \end{subfigure}  
-  \begin{subfigure}{0.45\textwidth}
-  \centering
-  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
-  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
-  \end{subfigure}  
-  \caption{1D correlation functions of the center of masses of aromatic head
-	  groups, $g(z)$, show decaying oscillatory behavior and have consistent
-	  correlation lengths with experiment. We calculated the correlation length by
-	  fitting a decaying exponential function
-	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
-	  correlation length is longer for ordered basin systems
-	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
-	  correlation length for (d) because there are no clear peaks. We assume that
-	  this correlation length is less than the vertical distance between
-	  monomers.}\label{fig:correlation}
-  \end{figure}
+  % Moved to supporting info
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \centering
+%  \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
+%  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
+%  \end{subfigure}  
+%  \begin{subfigure}{0.45\textwidth}
+%  \centering
+%  \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
+%  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
+%  \end{subfigure}  
+%  \begin{subfigure}{0.45\textwidth}
+%  \centering
+%  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
+%  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
+%  \end{subfigure}  
+%  \begin{subfigure}{0.45\textwidth}
+%  \centering
+%  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
+%  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
+%  \end{subfigure}  
+%  \caption{1D correlation functions of the center of masses of aromatic head
+%	  groups, $g(z)$, show decaying oscillatory behavior and have consistent
+%	  correlation lengths with experiment. We calculated the correlation length by
+%	  fitting a decaying exponential function
+%	  (Equation~\ref{eqn:decaying_exponential}) to the peaks of $g(z)$. The
+%	  correlation length is longer for ordered basin systems
+%	  (Table~\ref{table:correlation_length}). We did not attempt to calculate the
+%	  correlation length for (d) because there are no clear peaks. We assume that
+%	  this correlation length is less than the vertical distance between
+%	  monomers.}\label{fig:correlation}
+%  \end{figure}
 
@@
   several reasons. Experimental peaks broaden due to effects that we can not
-  easily simulate such as finite size crystalline domains and instrumental % reference needed
+  easily simulate such as finite size crystalline domains and instrumental
   resolution~\cite{girolami_x-ray_2016}. In our simulated XRD patterns, 
@@
 
-  Increasing thermal noise in the $z$-direction will reduce the intensity
-  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increased the
-  thermal noise of the simplified parallel displaced system in the $z$-direction by
-  12\% and 27\%, we saw a 3 and 15-fold decrease in the maximum intensity of 
-  R-$\pi$ respectively (Figure~\ref{fig:intensity_vs_zsigma}). Despite the decrease in 
-  intensity, the 3 cross-sections have the same shape 
-  (Figure~\ref{fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
-  not consistent with experiment.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
-  \caption{}\label{fig:intensity_vs_zsigma}
-  \end{subfigure}
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
-  \caption{}\label{fig:rpi_xsection_vs_zsigma}
-  \end{subfigure}
-  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
-  thermal noise in the $z$-direction; however, the $q_r$ cross-section profile does
-  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
-  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
-  background intensity, relative to systems with simulation levels of disorder (blue)
-  by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor 
-  of 15 when we increase $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
-  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
-  \end{figure}
-
-  However, when we allowed monomer columns to move independently in the
+%  Increasing thermal noise in the $z$-direction will reduce the intensity
+%  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increased the
+%  thermal noise of the simplified parallel displaced system in the $z$-direction by
+%  12\% and 27\%, we saw a 3 and 15-fold decrease in the maximum intensity of 
+%  R-$\pi$ respectively (Figure~\ref{fig:intensity_vs_zsigma}). Despite the decrease in 
+%  intensity, the 3 cross-sections have the same shape 
+%  (Figure~\ref{fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
+%  not consistent with experiment. 
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.49\textwidth}
+%  \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
+%  \caption{}\label{fig:intensity_vs_zsigma}
+%  \end{subfigure}
+%  \begin{subfigure}{0.49\textwidth}
+%  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
+%  \caption{}\label{fig:rpi_xsection_vs_zsigma}
+%  \end{subfigure}
+%  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
+%  thermal noise in the $z$-direction; however, the $q_r$ cross-section profile does
+%  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
+%  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
+%  background intensity, relative to systems with simulation levels of disorder (blue)
+%  by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor 
+%  of 15 when we increase $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
+%  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
+%  \end{figure}
+
+  When we allow simplified monomer columns to move independently in the
   $z$-direction, the intensity of R-$\pi$ drops and the $q_r$ cross-section of
-  the simulated diffraction patterns smooths out. We can demostrate this by
+  the simulated diffraction patterns smooths out. We can demonstrate this by
   creating a simplified sandwiched configuration (as described above), with
@@
 
+  %BJC: I could move the following paragraph to supporting information since it
+  % relies on a qualitative comparison between the following figure and the 
+  % the original correlation functions which I moved to supporting already.
   It therefore seems likely that the discrepancy between the shape and intensity of
@@
 
-  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
-  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a
-  system with uncorrelated columns, we modified the disorder in both the $r$ and
-  $\theta$ directions by multiplying their values by a factor of 0.5 and 2
-  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
-  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
-  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
-  with experiment, meaning the quenched configuration contains about the right
-  amount of disorder on the $xy$ plane. However, the relatively low quality of
-  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
-  simulation might not be the best comparison to experiment and that some form of
-  initial configuration dependence causes extra structure.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
-  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
-	  FWHM of the $q_r$ cross-section of R-$\pi$. When we cut the amount of $r$ and
-	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
-	  we double the disorder (Noise factor = 2), the FWHM decreases by
-	  51\%.}\label{fig:qy_fwhm}
-  \end{figure}
+  We also used our simplified systems in order to study the influence of increased
+  disorder in each dimension. Increasing $z$-directional disorder reduces the
+  intensity of R-$\pi$ without changing the shape of its $q_r$ cross-section.
+  Increasing disorder on the $xy$ plane, somewhat counterintuitively, reduces
+  the FWHM of the $q_r$ cross-section of R-$\pi$ with an insignificant effect
+  on its intensity. We explain these points in more depth in 
+  Section~\ref{S-section:simplified_sf}.
+
+%  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
+%  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a
+%  system with uncorrelated columns, we modified the disorder in both the $r$ and
+%  $\theta$ directions by multiplying their values by a factor of 0.5 and 2
+%  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
+%  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
+%  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
+%  with experiment, meaning the quenched configuration contains about the right
+%  amount of disorder on the $xy$ plane. However, the relatively low quality of
+%  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
+%  simulation might not be the best comparison to experiment and that some form of
+%  initial configuration dependence causes extra structure.
+%
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
+%  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
+%	  FWHM of the $q_r$ cross-section of R-$\pi$. When we cut the amount of $r$ and
+%	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
+%	  we double the disorder (Noise factor = 2), the FWHM decreases by
+%	  51\%.}\label{fig:qy_fwhm}
+%  \end{figure}
 
@@
   The ether dihedrals become decorrelated on a reasonable timescale when we raise
-  the system temperature. At 300 K (Figure~\ref{fig:dihedrals_300K}), the autocorrelation function does
+  the system temperature. At 300 K (Figure~\ref{S-fig:dihedrals_300K}), the autocorrelation function does
   not cross the $x$-axis until $\sim$105 ns meaning that tails fully rotate on average about 
@@
   decorrelation of the ether dihedrals after $\sim$11 ns with a plateau at 0, 
-  (Figure~\ref{fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
+  (Figure~\ref{S-fig:dihedrals_500K}) indicating a complete loss of memory. We annealed
   the resultant configuration back down to 300 K over 200 ns to see if the increased rotational
@@
 
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  	\centering
-  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.pdf}
-  	\caption{300K}\label{fig:dihedrals_300K}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  	\centering
-  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.pdf} % Run : torsions.py -t tethered_columns.xtc -g tethered_columns.gro (the appropriate dihedral is the default)
-  	\caption{500K}\label{fig:dihedrals_500K}
-  \end{subfigure}
-  \caption{The outer tail ether dihedrals become decorrelated on a reasonable
-  timescale when we raise the system temperature. (a) The dihedrals do not
-  become decorrelated for ca. 100 ns when the system is equilibrated at 300 K.
-  (b) The ether dihedrals become decorrelated after 11 ns when the temperature
-  of the system is increased to 500 K.}\label{fig:dihedrals}
-  \end{figure}
+  %BJC: moved to SI
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  	\centering
+%  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.pdf}
+%  	\caption{300K}\label{fig:dihedrals_300K}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  	\centering
+%  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.pdf} % Run : torsions.py -t tethered_columns.xtc -g tethered_columns.gro (the appropriate dihedral is the default)
+%  	\caption{500K}\label{fig:dihedrals_500K}
+%  \end{subfigure}
+%  \caption{The outer tail ether dihedrals become decorrelated on a reasonable
+%  timescale when we raise the system temperature. (a) The dihedrals do not
+%  become decorrelated for ca. 100 ns when the system is equilibrated at 300 K.
+%  (b) The ether dihedrals become decorrelated after 11 ns when the temperature
+%  of the system is increased to 500 K.}\label{fig:dihedrals}
+%  \end{figure}
 

### 2018-11-17 Ben_Manuscripts/structure_paper/supporting_information.tex
Working on response to reviewers

@@
 
-  We chose to build all systems using 20 monomers per column, i.e.
-for a simulation with 5 columns around each pore, there are 100 monomers per pore, and 400 monomers per simulation.
-We made this choice
+  We chose to build all systems using 20 monomers per column, i.e. for a simulation with 5 
+  columns around each pore, there are 100 monomers per pore, and 400 monomers per simulation.  We made this choice
   by considering a number of factors that directly affect the quality of our results. 
@@
   between stacked monomers persist throughout the entire correlation function (see
-  Figure~\ref{M-fig:correlation} of the main text). The correlation function of the system which we
+  Figure~\ref{fig:correlation}). The correlation function of the system which we
   built with 40 monomers per column is very similar to that created with 20 monomers
-  per columns (continues to oscillate for its full length
+  per column (it continues to oscillate for its full length
   (Figure~\ref{fig:tall_correlation_full})). If we continue adding monomers, the 
@@
 
+  \section{Correlation Functions}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
+  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
+  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
+  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
+  \end{subfigure}  
+  \begin{subfigure}{0.45\textwidth}
+  \centering
+  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
+  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
+  \end{subfigure}  
+  \caption{1D correlation functions of the center of masses of aromatic head
+	  groups, $g(z)$, show decaying oscillatory behavior and have consistent
+	  correlation lengths with experiment. We calculated the correlation length by
+	  fitting a decaying exponential function
+	  (Equation~\ref{M-eqn:decaying_exponential} of the main text) to the peaks of $g(z)$. The
+	  correlation length is longer for ordered basin systems
+	  (Table~\ref{M-table:correlation_length} of the main text). We did not attempt to calculate the
+	  correlation length for (d) because there are no clear peaks. We assume that
+	  this correlation length is less than the vertical distance between
+	  monomers.}\label{fig:correlation}
+  \end{figure}
+
+  \section{Structure factors of simplified systems}\label{section:simplified_sf}
+
+  In the Section~\ref{M-section:rpi} of the main text, we used simplified systems
+  made up of point scatterers in order to understand the main factors that influence
+  the cross-sections of R-$\pi$. We showed that both the shape and the intensity
+  of R-$\pi$ are strongly influenced by the degree of correlation between columns.
+  Here we show the influence of varied amounts of noise on the $xy$ plane and in
+  the $z$-direction for select cases.
+
+  Increasing thermal noise in the $z$-direction will reduce the intensity
+  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increased the
+  thermal noise of the simplified parallel displaced system with fully correlated
+  columns in the $z$-direction by 12\% and 27\%, we saw a 3 and 15-fold decrease in
+  the maximum intensity of R-$\pi$ respectively (Figure~\ref{fig:intensity_vs_zsigma}).
+  Despite the decrease in intensity, the 3 cross-sections have the same shape 
+  (Figure~\ref{fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
+  not consistent with experiment.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
+  \caption{}\label{fig:intensity_vs_zsigma}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
+  \caption{}\label{fig:rpi_xsection_vs_zsigma}
+  \end{subfigure}
+  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing
+  thermal noise in the $z$-direction; however, the $q_r$ cross-section profile does
+  not change. (a) The intensity of R-$\pi$ drops precipitously as we increase
+  $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the
+  background intensity, relative to systems with simulation levels of disorder (blue)
+  by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor 
+  of 15 when we increase $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
+  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
+  \end{figure}
+
+  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$
+  cross-section of R-$\pi$ to, somewhat counterintuitively, decrease. Using a
+  system with uncorrelated columns, we modified the disorder in both the $r$ and
+  $\theta$ directions by multiplying their values by a factor of 0.5 and 2
+  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
+  by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
+  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
+  with experiment, meaning the quenched configuration contains about the right
+  amount of disorder on the $xy$ plane. However, the relatively low quality of
+  the fit implies that the FWHM of a fixed Lorentzian fit to data from a single
+  simulation might not be the best comparison to experiment and that some form of
+  initial configuration dependence causes extra structure.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{qy_fwhm.pdf}
+  \caption{Increasing the amount of disorder in the $xy$ plane decreases the
+	  FWHM of the $q_r$ cross-section of R-$\pi$. When we cut the amount of $r$ and
+	  $\theta$ disorder in half (Noise factor = 0.5), the FWHM increases by 88\%. When
+	  we double the disorder (Noise factor = 2), the FWHM decreases by
+	  51\%.}\label{fig:qy_fwhm}
+  \end{figure}
+
   \section{Ensemble of ordered sandwiched configurations}\label{section:sandwiched_ensemble}
@@
   autocorrelation function of the outer tail either dihedrals pictured
-  in Figure~\ref{fig:dihedrals}.
+  in Figure~\ref{fig:dihedral_illustration}. The plots of the autocorrelation
+  functions versus time lag are shown in Figure~\ref{fig:dihedral}.
 
@@
   since the position of the center tail leads to fundamentally different interactions and
-  dynamics.}\label{fig:dihedrals}
+  dynamics.}\label{fig:dihedral_illustration}
+  \end{figure}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.pdf}
+  	\caption{300K}\label{fig:dihedrals_300K}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  	\centering
+  	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.pdf} % Run : torsions.py -t tethered_columns.xtc -g tethered_columns.gro (the appropriate dihedral is the default)
+  	\caption{500K}\label{fig:dihedrals_500K}
+  \end{subfigure}
+  \caption{The outer tail ether dihedrals become decorrelated on a reasonable
+  timescale when we raise the system temperature. (a) The dihedrals do not
+  become decorrelated for ca. 100 ns when the system is equilibrated at 300 K.
+  (b) The ether dihedrals become decorrelated after 11 ns when the temperature
+  of the system is increased to 500 K.}\label{fig:dihedral}
   \end{figure}

### 2018-11-18 Ben_Manuscripts/structure_paper/response_to_reviewers.tex
Added many responses to Reviewer 1. Outlined else needs to be done

@@
 
-	\item \begin{quote} \textit{This manuscript describes atomistic molecular dynamics simulations and
-	diffraction analysis of hexagonally-arranged pores, each of which is made of many columns of the 
-	monomer Na-GA3C11. This physical system is of interest because such nanopores have potential to 
-	transform filtration applications. This work is of potential interest to the JPC readership because
-	it provides atomistic insight into the origins of diffraction reflections observed in experiments, 
-	which could be used to resolve discrepancies about what the structure of these hexagonal arrays are,
-	or used to engineer better filters. Overall, the manuscript provides comprehensive descriptions of
-	metrics used to evaluate the simulated structures against experiments, but the number of things
-	described and length of these descriptions obscures whether significant new physical insight into
-	this system is made.} \end{quote}
+    \item \begin{quote} \textit{This manuscript describes atomistic molecular
+	    dynamics simulations and diffraction analysis of hexagonally-arranged pores,
+	    each of which is made of many columns of the monomer Na-GA3C11. This physical
+	    system is of interest because such nanopores have potential to transform
+	    filtration applications. This work is of potential interest to the JPC
+	    readership because it provides atomistic insight into the origins of
+	    diffraction reflections observed in experiments, which could be used to resolve
+	    discrepancies about what the structure of these hexagonal arrays are, or used
+	    to engineer better filters. Overall, the manuscript provides comprehensive
+	    descriptions of metrics used to evaluate the simulated structures against
+	    experiments, but the number of things described and length of these
+	    descriptions obscures whether significant new physical insight into this system
+	    is made.} 
+    \end{quote}
 
@@
 
-	Author reply: We agree with the reviewer that 5-columns per core is more plausible than 4 and that much
+    Author reply: We agree with the reviewer that 5 columns-per-core is more plausible than 4 and that much
     longer simulations may provide further supporting evidence. However, there is very little motion on
-    the hundreds of nanoseconds timescale which we simulated which suggests that we will not gain any 
+    the hundreds of nanoseconds timescale that we simulated which suggests that we will not gain any 
     significant new insight by extending our simulations into the microsecond regime. It is not feasible 
@@
     with experimental pore spacing. As mentioned in the text, the vertical stacking distance between monomers
-    in that system is far too large. The columns are `stretch' in the $z$-direction allowing the pores take
+    in that system is far too large. The columns are `stretched' in the $z$-direction allowing the pores take
     up less space on the $xy$ plane and thus pack closer together.
@@
 
-    Author reply: The reviewer makes good points about R-double that need to be clarified in the main text.
-    R-double appears in a dry system with non-uniformly spaced monomers. However, such a system is only 
-    stable, as we've modeled it, if $z$-direction position restraints are applied to monomer head groups. As
-    soon as the restraints are released, R-double fades and the monomer spacing becomes uniform. We believe 
-    that water facilitates the appearance of R-double by stabilizing non-uniform spacing through hydrogen bonding,
-    as the reviewer suggests. We re-performed the scattering analysis on the same system with water molecules
-    removed, as suggested, and R-double is still present.
+    Author reply: We thank the reviewer for exposing a potentially unclear
+    explanation of the origin of R-double. R-double appears in a dry system with
+    non-uniformly spaced monomers \textit{only} if $z$-direction position
+    restraints are applied to monomer head groups in order to maintain unevenly
+    spaced stacking. As soon as the restraints are released, R-double fades and the
+    monomer spacing becomes uniform. We modified the text on page _ in order to more
+    clearly convey this message:
 
-    % BJC: mention that this plot is added to supporting info and that the "head group removed" figure further
-    % supports this conclusion.
+    Old text: ``We can also produce R-double if the LLC monomers are not
+    uniformly spaced in the $z$-direction, but instead form pairs that stack less
+    than 3.7~\AA~apart, with COMs that are spaced 7.4 \AA~ from neighboring pairs
+    of monomers (Figure~\ref{fig:staggered_rzplot_norestraints}).  Our force field
+    causes our system to tend towards uniformly spaced layers. Simulations of
+    unevenly spaced systems are only stable if position restraints are applied to
+    heavy atoms of the phenyl rings. Additionally, there is little evidence from QM
+    studies of stacked $\pi-\pi$ systems that such uneven stacking could be
+    energetically stable.~\cite{tauer_beyond_2005}"
+
+    New text: ``We can also produce R-double if the LLC monomers are not
+    uniformly spaced in the $z$-direction, but instead are placed in pairs that
+    stack less than 3.7~\AA~apart, with COMs that are spaced 7.4 \AA~ from
+    neighboring pairs of monomers (Figure~\ref{fig:staggered_rzplot_norestraints}).
+    Simulations of unevenly spaced systems are only stable while position
+    restraints are applied to heavy atoms of the phenyl rings. There is little
+    evidence from quantum mechanical studies of stacked $\pi-\pi$ systems that such
+    uneven stacking could be energetically stable.~\cite{tauer_beyond_2005} As soon
+    as we remove position restraints, our system to tends towards uniformly spaced
+    monomers."
+
+    R-double is only long-term stable without position restraints if a small
+    amount of water is present. We believe that water facilitates the appearance
+    of R-double by stabilizing non-uniform spacing through hydrogen bonding, as the
+    reviewer suggests. We clarified the text on page _ in order to make this 
+    conclusion clear:
+
+    Old text: ``When two vertically stacked monomer head groups hydrogen bond
+    with a shared water molecule, the monomers are drawn closer together (as
+    illustrated in Figure~\ref{fig:hbond_visualization}), which creates an
+    asymmetry that allows R-double to appear. If a monomer head group shares a
+    hydrogen-bonded water molecule with a head group above itself, it will be less
+    likely to share a water molecule with a head group below it due to geometric
+    constraints. The monomer head group below can just as easily share a water
+    molecule with a head group below itself. In this scenario, the COMs of each
+    pair are 2 times the $\pi$-stacking distance apart which would lead to R-double
+    (much like the configuration in
+     Figure~\ref{fig:staggered_rzplot_norestraints}). There are a modest number of
+    occurrences of this scenario, which we quantify in further detail in the SI,
+    Section \ref{S-section:rdouble}."
+
+    New text: ``The addition of a small amount of water to the pores stabilizes
+    non-uniform stacking of head groups much like that shown in
+    Figure~\ref{fig:staggered_rzplot_norestraints}. When two vertically stacked
+    monomer head groups hydrogen bond with a shared water molecule, the monomers
+    are drawn closer together (as illustrated in
+    Figure~\ref{fig:hbond_visualization}), which creates the asymmetry that allows
+    R-double to appear. If a monomer head group shares a hydrogen-bonded water
+    molecule with a head group above itself, it will be less likely to share a
+    water molecule with a head group below it due to geometric constraints. The
+    monomer head group below can just as easily share a water molecule with a head
+    group below itself. There are a modest number of occurrences of this scenario,
+    which we quantify in further detail in the SI, Section
+    \ref{S-section:rdouble}."
+
+    The reviewer asked us to re-perform the scattering analysis on the same
+    system with water molecules removed. We would like to emphasize that we
+    attempted to make a similar argument by removing just the head group atoms from
+    the trajectory and re-performing the scattering analysis
+    (Figure~\ref{M-fig:rdouble_nophenyls}). In the absence of head groups, R-double
+    is not present, implying that their structure (which is influenced by the
+    presence of water molecules) is responsible for the R-double reflection. For
+    completeness, we performed the scattering analysis on the same system with
+    water molecules removed, as suggested by the reviewer, and R-double is still
+    present. This is the expected result since the structure of water itself does
+    not give rise to R-double. We've added the resulting simulated XRD pattern to
+    the Supporting Information, Figure~\ref{S-TBD}.
 
@@
 
+    Author reply: We thank the reviewer for their suggestion. We do not deny
+    that the tilt of the monomer tails is a plausible explanation for the
+    appearance of reflections that resemble R-spots in many liquid crystal systems.
+    While the reviewer's suggested experiment is a good idea, its results in this
+    case are ambiguous for a couple reasons. First, the tails may still pack
+    hexagonally in the tilted configuration which would independently give rise to
+    R-spots. Second, it is necessary to impose high force constant (>1000 kJ mol
+    nm$^{-2}$) position restraints in order to maintain a tilt angle close to that
+    implied by the 2D WAXS data. The resulting high degree of order in the system 
+    gives way to reflections which are easily misinterpretted. We have added the
+    following text highlighted in red to the text shown on Page _ in order to
+    acknowledge that tail tilt is a valid explanation of R-spot-like reflections 
+    and to offer a reason a molecular reason why our monomers in our system do not
+    tilt:
+
+    Modified text: ``Previous literature has attributed the R-spots reflection
+    in this particular WAXS dataset as the result of tilted alkane
+    chains~\cite{feng_scalable_2014}. {\color{red} This explanation is not
+    unfounded as there are examples in literature of systems where tilted liquid
+    crystals give rise to reflections that resemble R-spots (Cite, Cite).} We
+    measured the tilt angle of the alkane chains of the 280 K system by measuring
+    the angle made by the vector extending from top to bottom of each tail with
+    respect to the membrane plane.  We found that it equilibrates to an average
+    tilt angle of -2 $\pm$ 13\degree~(Figure~\ref{fig:tilt}), far from the
+    37\degree~tilt angle previously used to explain R-spots. Even when we placed
+    position restraints on the monomers in a tilted initial configuration, monomers
+    quickly reduced their tilt relative to the $xy$ plane to an angle statisically
+    indistinguishable from zero (see Section \ref{S-section:tail_tilt} of the SI).
+    {\color{red} While it is plausible that our force field may in part be
+    responsible for the tendency of monomers to stay nearly flat, the monomer tails
+    lack the functional groups which are known to facilitate tail tilting (cite).}"
+
     \item \begin{quote}
-    \textit{These arguments would be stronger if there weren't so many qualifications about simulation 
-    timescales and GAFF, in particular its ability to predict the shortest-scale feature (pi-stacking) for 
-    this system. How does everything else change if the force-field were tuned to get that feature correct?}
+    \textit{These arguments would be stronger if there weren't so many
+	    qualifications about simulation timescales and GAFF, in particular its ability
+	    to predict the shortest-scale feature (pi-stacking) for this system. How does
+	    everything else change if the force-field were tuned to get that feature
+	    correct?}
     \end{quote}
 
+    Author reply: We thank the reviewer for their constructive criticism. Many
+    of our findings may be relatively independent of the force fields used, but we
+    feel that we should include these qualifications in order to not overstate our
+    case. It is common for researchers to run simulations for an insufficient
+    length of time and to make bold claims. We acknowledge the shortcomings of our
+    techniques in order to inspire other researchers to build on our initial work.
+
+    We agree with the reviewer that we could tune our force field in order to
+    exactly reproduce the $\pi-\pi$ stacking distance seen experimentally. Surely
+    there will be some structural differences. There are many ways to tune a force
+    field in order to achieve this. We prefer to work with an "out-of-the-box"
+    force field since they are widely used and can be applied to vast number of
+    systems. The ultimate goal of our work is to create new monomers that can
+    achieve specfic separations.  If we can gain experimentally-consistent insights
+    using our model simulated with GAFF, then we can have increased confidence in
+    future predictions generated from systems built with unsynthesized monomers.
+    With that said, we think that it would be interesting to repeat our analysis
+    using different and/or optimized force fields in a future study in order to
+    comment on the signficance of any differences.
+
+    %BJC: Emphasize main goal in intro (or pull a quote that says it)
+    %BJC: add justification of gaff to methods?
+    %BJC: Add force field optimization to future work
+
     \item \begin{quote}
-    \textit{The MD-Structure-Factor repository is not available at the provided github link, nor does it appear
-    to be online anywhere. So, the correctness of that code cannot be checked.}
+    \textit{The MD-Structure-Factor repository is not available at the provided
+	    github link, nor does it appear to be online anywhere. So, the correctness of
+	    that code cannot be checked.}
     \end{quote}
 
-	Author reply: We thank the reviewer for pointing this out and apologize for this mistake. The referenced
-	GitHub repository was set to private by our collaborators but has now been made public. Please feel 
-	free to read through the code.
+    Author reply: We thank the reviewer for pointing this out and apologize for
+    our mistake. The referenced GitHub repository was set to private due to
+    miscommunication with our collaborators but it has now been made public. Please
+    feel free to read through the code. We have performed checks to ensure that the
+    code works properly, especially when simulating monoclinic unit cells. For
+    example, we generated test trajectories containing thousands of frames made up
+    of configurations of randomly placed point scatterers in a monoclinic unit cell.
+    We expect that the simulated diffraction pattern will have a gaussian shape.
+    This exact result is shown in the Figure S-thingy of the supporting information.
+    With improper treatment of the monoclinic geometry, the gaussian shape is
+    skewed into an elliptical shape.
 
     \item \begin{quote}
-    \textit{One might want to check that code based on Figure 7f, where presumably spherical scatterers 
-    generate reflections with anisotropy (diamonds instead of squares or circles). This kind of an artefact
-    is plausible if there are errors handling the non-cubic box, or with scattering angles that aren't parallel
-    to a box axis. llcsim/analysis/correlation.py looks like it has the machinery for doing the scattering analysis.}
+    \textit{One might want to check that code based on Figure 7f, where
+	    presumably spherical scatterers generate reflections with anisotropy (diamonds
+	    instead of squares or circles). This kind of an artefact is plausible if there
+	    are errors handling the non-cubic box, or with scattering angles that aren't
+	    parallel to a box axis. llcsim/analysis/correlation.py looks like it has the
+	    machinery for doing the scattering analysis.}
     \end{quote}
 
-	Author reply: We thank the reviewer for their astute observation and the resulting improvements to 
-	our manuscript.	We generated Figure 7f by calculating the structure factor of a 2-dimensional array of 
-	hexagonally-packed scatterers. It is meant to be a simplified representation of the scattering exhibited
-	by hexagonally packed alkane tails so that we can qualitatively understand where we would expect R-spots to appear if 
-	tails indeed pack in that way. Since it is possible to generate a rectangular unit cell which contains 
-	hexagonally packed point scatterers, there are no artifacts due to improper treatment of periodicity. 
-	Although we believe our calculations are correct, we originally used only eight total scatterers in the 
-	2D unit cell and then plotted the structure factor with a contour plot (\texttt{matplotlib.pyplot.contourf})
-	which does not interpolate the data. We re-created Figure 7f by simulating the structure factor of 100 
-	hexagonally packed scatterers, in order to get higher fourier space resolution, and then plotting the
-	result with \texttt{matplotlib.pyplot.imshow} and Gaussian interpolation. We have added the code used to
-	generate this figure to the \texttt{llcsim} repository which can be accessed at 
+    Author reply: We thank the reviewer for their astute observation and
+    the resulting improvements to our manuscript. We generated Figure 7f by
+    calculating the structure factor of a 2-dimensional array of hexagonally-packed
+    scatterers. It is meant to be a simplified representation of the scattering
+    exhibited by hexagonally packed alkane tails so that we can qualitatively
+    understand where we would expect R-spots to appear if tails indeed pack in that
+    way. Since it is possible to generate a rectangular unit cell which contains
+    hexagonally packed point scatterers, there are no artifacts due to improper
+    treatment of periodicity.  Although we believe our calculations are correct, we
+    originally used only eight total scatterers in the 2D unit cell and then
+    plotted the structure factor with a contour plot
+    (\texttt{matplotlib.pyplot.contourf}) which does not interpolate the data. We
+    re-created Figure 7f by simulating the structure factor of 100 hexagonally
+    packed scatterers, in order to get higher fourier space resolution, and then
+    plotting the result with \texttt{matplotlib.pyplot.imshow} and Gaussian
+    interpolation. We have added the code used to generate this figure to the
+    \texttt{llcsim} repository which can be accessed at
     \texttt{https://github.com/bencoscia/llcsim/blob/master/analysis/hexagonal\_packing.py}.
@@
     \item \begin{quote}	
-    \textit{Regarding the ion conductivities, how do the numbers presented here compare against ion conductivities
-    predicted with GAFF and other polarizable and nonpolarizable force fields? If GAFF is systematically too high
-    in other cases, it could help explain the order-of-magnitude discrepancy observed here.}
+    \textit{Regarding the ion conductivities, how do the numbers presented here
+	    compare against ion conductivities predicted with GAFF and other polarizable
+	    and nonpolarizable force fields? If GAFF is systematically too high in other
+	    cases, it could help explain the order-of-magnitude discrepancy observed here.}
     \end{quote}

### 2018-11-18 Ben_Manuscripts/structure_paper/Final_Draft.tex
Added many responses to Reviewer 1. Outlined else needs to be done

@@
   WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
-  We measured the tilt angle of the alkane chains of the 280 K system by measuring
-  the angle made by the vector extending from top to bottom of each tail with
-  respect to the membrane plane. We found that it equilibrates to an average tilt
-  angle of -2 $\pm$ 13\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle
-  previously used to explain R-spots. Even when we placed position restraints on
-  the monomers in a tilted initial configuration, monomers quickly reduced their
-  tilt relative to the $xy$ plane to an angle statisically indistinguishable from
-  zero (see Section \ref{S-section:tail_tilt} of the SI).
+  This explanation is not unfounded as there are examples in literature of
+  systems where tilted liquid crystals give rise to reflections that resemble
+  R-spots (Cite, Cite). We measured the tilt angle of the alkane chains of the
+  280 K system by measuring the angle made by the vector extending from top to
+  bottom of each tail with respect to the membrane plane. We found that it
+  equilibrates to an average tilt angle of -2 $\pm$
+  13\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
+  used to explain R-spots. Even when we placed position restraints on the
+  monomers in a tilted initial configuration, monomers quickly reduced their tilt
+  relative to the $xy$ plane to an angle statisically indistinguishable from zero
+  (see Section \ref{S-section:tail_tilt} of the SI). While it is plausible that 
+  our forcefield may in part be responsible for the tendency of monomers to stay
+  nearly flat, the monomer tails lack the functional groups which are known to
+  facilitate tail tilting.
 
@@
 
-  We can also produce R-double if the LLC monomers are not uniformly spaced in the
-  $z$-direction, but instead form pairs that stack less than 3.7~\AA~apart, with
-  COMs that are spaced 7.4 \AA~ from neighboring pairs of monomers 
-  (Figure~\ref{fig:staggered_rzplot_norestraints}). 
-  Our force field causes our system to tend towards uniformly spaced layers.
-  Simulations of unevenly spaced systems are only stable if position restraints
-  are applied to heavy atoms of the phenyl rings.  Additionally, there is little
-  evidence from QM studies of stacked $\pi-\pi$ systems that such uneven stacking
-  could be energetically stable.~\cite{tauer_beyond_2005}
-
-  The addition of water to the system promotes the appearance of R-double, providing
-  an answer to Question~\ref{point:water} posed in the introduction.
+  We can also produce R-double if the LLC monomers are not uniformly spaced in
+  the $z$-direction, but instead are placed in pairs that stack less than
+  3.7~\AA~apart, with COMs that are spaced 7.4 \AA~ from neighboring pairs of
+  monomers (Figure~\ref{fig:staggered_rzplot_norestraints}). Simulations of
+  unevenly spaced systems are only stable while position restraints are applied
+  to heavy atoms of the phenyl rings. There is little evidence from quantum
+  mechanical studies of stacked $\pi-\pi$ systems that such uneven stacking could
+  be energetically stable.~\cite{tauer_beyond_2005} As soon as we remove position
+  restraints, our system to tends towards uniformly spaced monomers.
+
+  The addition of water to the system promotes the appearance of R-double,
+  providing an answer to Question~\ref{point:water} posed in the introduction.
   We added water to the parallel displaced and sandwiched configurations in the
@@
   produce that shown in Figure~\ref{fig:rdouble_nophenyls}. R-double does not
-  appear without the presence of the head groups. Water molecules must therefore play a
-  role in the structuring of the head groups in these simulations since R-double does not appear in
-  any dry simulations.
-
-  When two vertically stacked monomer head groups hydrogen bond with a shared
-  water molecule, the monomers are drawn closer together (as illustrated in
-  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows
+  appear without the presence of the head groups. Water molecules must therefore
+  play a role in the structuring of the head groups in these simulations since
+  R-double does not appear in any dry simulations.
+
+  %BJC: old text:
+%  When two vertically stacked monomer head groups hydrogen bond with a shared
+%  water molecule, the monomers are drawn closer together (as illustrated in
+%  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows
+%  R-double to appear. If a monomer head group shares a hydrogen-bonded water
+%  molecule with a head group above itself, it will be less likely to share a
+%  water molecule with a head group below it due to geometric constraints. The
+%  monomer head group below can just as easily share a water molecule with a head
+%  group below itself. In this scenario, the COMs of each pair are 2 times the
+%  $\pi$-stacking distance apart which would lead to R-double (much like the
+%  configuration in Figure~\ref{fig:staggered_rzplot_norestraints}). There are a
+%  modest number of occurrences of this scenario, which we quantify in further
+%  detail in the SI, Section \ref{S-section:rdouble}.
+
+  The addition of a small amount of water to the pores stabilizes non-uniform
+  stacking of head groups much like that shown in
+  Figure~\ref{fig:staggered_rzplot_norestraints}. When two vertically stacked
+  monomer head groups hydrogen bond with a shared water molecule, the monomers
+  are drawn closer together (as illustrated in
+  Figure~\ref{fig:hbond_visualization}), which creates the asymmetry that allows
   R-double to appear. If a monomer head group shares a hydrogen-bonded water
@@
   monomer head group below can just as easily share a water molecule with a head
-  group below itself. In this scenario, the COMs of each pair are 2 times the
-  $\pi$-stacking distance apart which would lead to R-double (much like the
-  configuration in Figure~\ref{fig:staggered_rzplot_norestraints}). There are a
-  modest number of occurrences of this scenario, which we quantify in further
-  detail in the SI, Section \ref{S-section:rdouble}.
+  group below itself. There are a modest number of occurrences of this scenario,
+  which we quantify in further detail in the SI, Section \ref{S-section:rdouble}.
 

### 2018-11-18 Ben_Manuscripts/structure_paper/response_to_reviewers.tex
Updates

@@
 
-We thank the reviewers for carefully reading over our manuscript and providing helpful comments.
-We have taken the suggestions into consideration and made appropriate revisions to the manuscript document.
-All changes to the text have been documented below.
+We thank the reviewers for carefully reading over our manuscript and providing
+helpful comments. We have taken the suggestions into consideration and made
+appropriate revisions to the manuscript document. All changes to the text have
+been documented below.
 
@@
     \item \begin{quote}
-    \textit{As written, it is not clear if the authors are presenting this study as a validation of 
-	GAFF and the present equilibration techniques, or whether this study is providing significant new
-	physical insight into these lyotropic liquid crystals. The paper reads a bit more like the former,
-	with a comprehensive discussion of the degree to which five scattering features expected in 
-	experiments are predicted in simulations. However, at the same time, the authors make arguments
-	including (1) pores are made from five columns of monomers, (2) that water is present in the "dry"
-	structures, and (3) that a scattering feature comes from tail packing, not tilt: These observations
-	*could* be new physical insight into lyotropic liquid crystal structure, but as presented seem more
-	like hypotheses than conclusions:}
+    \textit{As written, it is not clear if the authors are presenting this
+	    study as a validation of GAFF and the present equilibration techniques, or
+	    whether this study is providing significant new physical insight into these
+	    lyotropic liquid crystals. The paper reads a bit more like the former, with a
+	    comprehensive discussion of the degree to which five scattering features
+	    expected in experiments are predicted in simulations. However, at the same
+	    time, the authors make arguments including (1) pores are made from five columns
+	    of monomers, (2) that water is present in the "dry" structures, and (3) that a
+	    scattering feature comes from tail packing, not tilt: These observations
+	    *could* be new physical insight into lyotropic liquid crystal structure, but as
+	    presented seem more like hypotheses than conclusions:}
+
+    \end{quote}
+
+    Author reply: We thank the reviewer for offering their interpretation
+    of the purpose of our study, as it is important that we properly convey our
+    message. The main purpose our work is to give a detailed description of the
+    structure of a lyotropic liquid crystal membrane backed by experimental data.
+    This work lays a foundation for future transport studies. By matching 2D-WAXS
+    data, we have attempted to unveil the most experimentally-consistent structure
+    possible. This is unlikely to be achieved if one assembled these systems using
+    united atom or coarse grained models due to the large number of potential
+    metastable configurational basins which plague a system like ours which exhibts
+    such slow dynamics.
+
+    We do not intend for this study to be a validation of GAFF for this
+    particular system. We believe we would come to similar conclusions using other
+    force fields, however validation of this hypothesis is left for a future study.
+    We chose GAFF because it is widely used to simulate organic molecules and there
+    are no force fields specifically built for our system. We are interested in
+    what information we can gain from an out-of-the-box force field and in future
+    work, we will validate whether GAFF is sufficient for reproducing trends in
+    experimental separation properties. Since our ultimate goal is to design new
+    monomers for solute-specific separations, we will be employing the same 
+    techniques used in this work to unsynthesized monomers. In most cases, we will
+    not have an experimental dataset to use for comparison. Despite all of the 
+    structural intracacies which we have revealed in this study, one of our main
+    conclusions is that regardless of which system we study, the radial distribution
+    of monomer components stays consistent. From this, we can hypothesize that 
+    we will extract similar transport results regardless of which configuration
+    we use to conduct transport studies. This is an extremely important finding
+    which may have been undersold in the original draft of the manuscript.
 

### 2018-11-18 Ben_Manuscripts/structure_paper/Final_Draft.tex
Updates

@@
 
-  Over the past 20 years, H\textsubscript{II}-phase LLC
-  polymer membrane studies have been limited primarily to the Na-GA3C11 monomer with some
-  characterization done after minor structural modifications. For example, 
-  Resel et al.~varied the length of the monomer tails and the counterion used and observed its effect
-  on pore spacing \cite{resel_structural_2000}.  In a later study of rejection
-  performance, it was shown that membranes formed by cross-linked Na-GA3C11 in
-  the H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in
-  diameter because the pores are too large \cite{zhou_supported_2005}. We do not
-  yet understand how to controllably reduce the effective pore size or how to
-  tune the chemical environment in the nanopores of this or related materials for
-  small molecule separations. The only source of predictive modeling for LLC
-  systems have been macroscopic models that likely do not adequately describe
-  transport at these length scales \cite{hatakeyama_water_2011}. Modeling with
-  molecular detail could provide sufficient information about the mechanisms and
-  chemical features to better inform experimental design of similar
-  nanostructured membranes.
+  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane
+  studies have been limited primarily to the Na-GA3C11 monomer with some
+  characterization done after minor structural modifications. For example, Resel
+  et al.~varied the length of the monomer tails and the counterion used and
+  observed its effect on pore spacing \cite{resel_structural_2000}. In a later
+  study of rejection performance, it was shown that membranes formed by
+  cross-linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes
+  less than 1.2 nm in diameter because the pores are too large
+  \cite{zhou_supported_2005}. We do not yet understand how to controllably reduce
+  the effective pore size or how to tune the chemical environment in the
+  nanopores of this or related materials for small molecule separations. The only
+  source of predictive modeling for LLC systems have been macroscopic models that
+  likely do not adequately describe transport at these length scales
+  \cite{hatakeyama_water_2011}. Modeling with molecular detail could provide
+  sufficient information about the mechanisms and chemical features to better
+  inform experimental design of similar nanostructured membranes.
+
+  % reworking paragraph
+  A molecular-level understanding of LLC polymer membrane structure, enabled by
+  molecular dynamics (MD) simulations, will enhance our understanding of the role
+  of monomer structure in solute transport and provide guidelines to reduce the
+  large chemical space available to design monomers for creation of
+  separation-specific membranes. It is important that we model the system with
+  a nanoscopic pore structure that is maximally consistent with experimental
+  data.
 
@@
   (see Section \ref{S-section:tail_tilt} of the SI). While it is plausible that 
-  our forcefield may in part be responsible for the tendency of monomers to stay
+  our force field may in part be responsible for the tendency of monomers to stay
   nearly flat, the monomer tails lack the functional groups which are known to

### 2018-11-19 Ben_Manuscripts/structure_paper/response_to_reviewers.tex
Text written

@@
 
-    Author reply: We thank the reviewer for offering their interpretation
-    of the purpose of our study, as it is important that we properly convey our
+    Author reply: We thank the reviewer for offering their interpretation of
+    the purpose of our study, as it is important that we properly convey our
     message. The main purpose our work is to give a detailed description of the
@@
     data, we have attempted to unveil the most experimentally-consistent structure
-    possible. This is unlikely to be achieved if one assembled these systems using
-    united atom or coarse grained models due to the large number of potential
-    metastable configurational basins which plague a system like ours which exhibts
-    such slow dynamics.
+    possible. To clarify this purpose, we have modified and added text to the
+    paragraph on page \_ of the introduction, in which we state our perceived
+    importance of knowing the most experimentally-consistent structure:
+
+    Old text: ``A molecular-level understanding of LLC polymer membrane
+    structure, enabled by molecular dynamics (MD) simulations, can provide
+    guidelines to reduce the large chemical space available to design monomers for
+    creation of separation-specific membranes. Useful molecular-level modeling
+    should incorporate a detailed picture of the nanoscopic pore structure, which
+    is crucial to understanding the role of monomer structure in solute transport
+    and membrane design.
+
+    New text: ``A molecular-level understanding of LLC polymer membrane
+    structure, enabled by molecular dynamics (MD) simulations, will enhance our
+    comprehension of the role of monomer structure in solute transport and provide
+    guidelines to reduce the large chemical space available to design monomers for
+    creation of separation-specific membranes. It is important that we model the
+    system with a nanoscopic pore structure that is maximally consistent with
+    experimental data in order to best approximate the chemical environment experienced
+    by solutes in future simulated transport studies."
+
+%This is unlikely to be achieved if one assembled these systems using
+%    united atom or coarse grained models due to the large number of potential
+%    metastable configurational basins which plague a system like ours which exhibts
+%    such slow dynamics.
 
@@
     We chose GAFF because it is widely used to simulate organic molecules and there
-    are no force fields specifically built for our system. We are interested in
-    what information we can gain from an out-of-the-box force field and in future
+    are no catch-all force fields built for liquid crystal systems. We are interested in
+    what information we can gain from a widely-used out-of-the-box force field and in future
     work, we will validate whether GAFF is sufficient for reproducing trends in
-    experimental separation properties. Since our ultimate goal is to design new
-    monomers for solute-specific separations, we will be employing the same 
-    techniques used in this work to unsynthesized monomers. In most cases, we will
-    not have an experimental dataset to use for comparison. Despite all of the 
-    structural intracacies which we have revealed in this study, one of our main
-    conclusions is that regardless of which system we study, the radial distribution
-    of monomer components stays consistent. From this, we can hypothesize that 
-    we will extract similar transport results regardless of which configuration
-    we use to conduct transport studies. This is an extremely important finding
-    which may have been undersold in the original draft of the manuscript.
+    experimental separation properties. To clarify our use of GAFF, we have added
+    the following text to Secton~\ref{method:parameterization} of the Methods on
+    page ~\pageref{method:parameterization}.
 
-    %BJC: want to convery that we want to reproduce all of the experimental features as best as possible
-	% using an out-of-the-box force field. That way we know we are approximating the chemical environment
-	% as close to the experimental system as possible. The goal is to eventually test large numbers of 
-	% monomers without the needing to dive into the excruciating detail shown here.
+    New text: ``We chose GAFF because it has been parameterized for use with
+    organic molecules. Although researchers have optimized force fields, including
+    GAFF (cite), for use with liquid crystals, they are often tuned in order to
+    reproduce one or more experimental observables. Since liquid crystals exist in
+    a wide range of shapes and sizes, including candidate monomers which we may
+    study, we chose to stick with a widely used force field. If we
+    can reproduce experimental trends using a single 'out-of-the-box' force field,
+    then there will be no need to complicate our studies with customized parameter
+    sets."
+
+    We have added the following citation:
+    %cite1: liquid crystal gaff tuned to get phase transition temperature.
+
+    Since our ultimate goal is to design new monomers for solute-specific
+    separations, we will be employing the same techniques used in this work to
+    unsynthesized monomers. In most cases, we will not have an experimental dataset
+    to use for comparison. Despite all of the structural intricacies which we have
+    revealed in this study, one of our main conclusions is that regardless of which
+    system we study, the radial distribution of monomer components stays
+    consistent. From this, we can hypothesize that we will extract similar
+    transport results regardless of which configuration we use to conduct
+    transport studies. This is an extremely important finding which may have
+    been undersold in the original draft of the manuscript. We have added the
+    following concluding paragraph the end of
+    Section~\label{section:pore_composition} on
+    page~\pageref{addition:pore_composition} in order to drive the point home:
+
+    New text: ``Our observations suggest that the details of transport may be
+    relatively independent of the structural differences between different possible
+    structures studied here. Despite the structural intricacies that give rise to
+    differences between the various metastable basins, all pores are characterized
+    by dense, primarily hydrophilic cores with a gradient towards a primarily
+    hydrophobic tail region far from the pore center. This implies that we might
+    see the same trends in transport properties from any of the systems studied so
+    far. Since the ultimate goal of our work is to design new monomers using high
+    throughput simulations, achieving that goal becomes tractable without the need
+    to optimize every system with an experimental dataset."
+
+    We also modified a paragraph in our conclusion on page \_ to better
+    emphasize our point:
+
+    Old text: ``We characterized the environment centered around the membrane
+    pores and learned that the pores are generally filled with monomer head groups
+    and sodium ions. All dry systems studied showed a similar distribution of
+    sodium, head groups and tails while the wet system shows evidence of slight
+    swelling, with minor changes in the distributions due to the presence of water
+    molecules. We also observed that there is not a hard partition between
+    hydrophilic and hydrophobic regions; instead, there is a gradient of chemical
+    constituents. This finding raises questions about the nature of size-exclusion
+    separations in systems without a well-defined pore size, which potentially
+    could enable separations that vary with chemical identity as well as size.
+
+    New text: ``Although exactly reproducing the experimental 2D-WAXS pattern
+    required attention to minute structural details, we found that all systems
+    showed similar radial distribution functions characterized by a gradual radial
+    transition from a dense hydrophlic core to hydrophobic tails. This observation
+    enables us to study new systems that have not been experimentally characterized
+    with the expectation that any additional structural optimization will not
+    greatly influence trends in transport property predictions. The compositional
+    gradient itself raises questions about the nature of size-exclusion separations
+    in systems without well-defined pore boundaries, which potentially could enable
+    separations that vary with chemical identity as well as size."
 
@@
     \item \begin{quote}
-    \textit{1. For the simulations performed here, the authors do make a strong case that 5 columns per
-    core gets the best pore-to-pore spacing (Figure 5). However, insufficient time is accessed to see 
-    whether the 4-, 5-, and 6-column initial conditions move towards or away from the expected pore 
-    spacing over many-microseconds trajectories. That said, for the quenches performed here, 5-columns
-    per core seems more plausible than 4.}
+    \textit{1. For the simulations performed here, the authors do make a strong
+	    case that 5 columns per core gets the best pore-to-pore spacing (Figure 5).
+	    However, insufficient time is accessed to see whether the 4-, 5-, and 6-column
+	    initial conditions move towards or away from the expected pore spacing over
+	    many-microseconds trajectories. That said, for the quenches performed here,
+	    5-columns per core seems more plausible than 4.}
     \end{quote}
 
-    Author reply: We agree with the reviewer that 5 columns-per-core is more plausible than 4 and that much
-    longer simulations may provide further supporting evidence. However, there is very little motion on
-    the hundreds of nanoseconds timescale that we simulated which suggests that we will not gain any 
-    significant new insight by extending our simulations into the microsecond regime. It is not feasible 
-    for us to carry out these simulations as it would consume our computational resources with little reward.
+    Author reply: We agree with the reviewer that 5 columns-per-core is more
+    plausible than 4 and that much longer simulations may provide further
+    supporting evidence. However, there is very little motion on the hundreds of
+    nanoseconds timescale that we simulated which suggests that we will not gain
+    any significant new insight by extending our simulations into the microsecond
+    regime. It is not feasible for us to carry out these simulations as it would
+    consume our computational resources with little reward.
     %BJC: The following might apply:
-    Some confusion may have been generated by agreement of the disordered basin 6 column-per-pore system
-    with experimental pore spacing. As mentioned in the text, the vertical stacking distance between monomers
-    in that system is far too large. The columns are `stretched' in the $z$-direction allowing the pores take
+    Some confusion may have been generated by agreement of the disordered basin
+    6 column-per-pore system with experimental pore spacing. As mentioned in the
+    text, the vertical stacking distance between monomers in that system is far too
+    large. The columns are `stretched' in the $z$-direction allowing the pores take
     up less space on the $xy$ plane and thus pack closer together.
@@
     \textit{Is this significant physical insight? It is insight, but the
-    authors do not make a compelling case for how 5 columns would change how we think about these crystals,
-    or how it would impact membrane engineering (or more importantly, whether these 5-column structures
-    assemble in the solution phase, or are only locally stable).}
+	    authors do not make a compelling case for how 5 columns would change how we
+	    think about these crystals, or how it would impact membrane engineering (or
+	    more importantly, whether these 5-column structures assemble in the solution
+	    phase, or are only locally stable).}
     \end{quote}
 
-    Author reply: We thank the reviewer for pushing us to provide more significant physical insight based
-    on the number of monomers per column. The number of columns-per-pore influences the pore radius which
-    is important for determining the limits of size-exclusion-based separations. It also tells use the 
-    density of interacting sites within the pore which may play a role in small molecule transport. We have
-    added the following text to the main document at the end of Section~\ref{M-section:mon_per_pore} on 
-    page _:
+    Author reply: We thank the reviewer for pushing us to provide more
+    significant physical insight based on the number of monomers per column. The
+    number of columns-per-pore influences the pore radius which is important for
+    determining the limits of size-exclusion-based separations. It also tells use
+    the density of interacting sites within the pore which may play a role in small
+    molecule transport. We have added the following text to the main document at
+    the end of Section~\ref{M-section:mon_per_pore} on page \_:
 
-    ``The number of columns per pore dictates the density of interaction sites within each pore and the 
-    pore radius. A higher number of interaction sites will surely play a role in transport of molecules
-    that have an affinity for the monomer head groups. 
-    %We measured the pore radius as the average distance from the pore center to each head group COM. 
-    The pore radius increases with the number of columns per pore (See Figure~\ref{S-fig:pore_radius}. 
-    This radius is likely related to the size of the molecules which can be excluded by this type of 
-    membrane. We may be able to control LLC membrane pore size by selecting monomers that are stable
-    in configurations with more columns-per-pore."
+    ``The number of columns per pore dictates the density of interaction sites
+    within each pore and the pore radius. A higher number of interaction sites will
+    surely play a role in transport of molecules that have an affinity for the
+    monomer head groups.  The pore radius increases with the number of columns per
+    pore (See Figure~\ref{S-fig:pore_radius}.  This radius is likely related to the
+    size of the molecules which can be excluded by this type of membrane. We may be
+    able to control LLC membrane pore size by selecting monomers that are stable in
+    configurations with more columns-per-pore."
 
     \item \begin{quote}
-    \textit{2. The authors make a pretty compelling case that water causes the R-double scattering feature
-    by showing its absence when water is added, but that the R-double appears and persists for 200ns after
-    the water makes its way into the crystal. However, the authors also show that nonuniformly spaced
-    monomers can give rise to the R-Double feature, a seeming counterexample to the necessity of water.
-    Is the R-double feature with water because the monomers are now irregularly spaced? What happens when
-    the waters are removed and the scattering re-performed in Fig 17c(bottom)?}
+    \textit{2. The authors make a pretty compelling case that water causes the
+    R-double scattering feature by showing its absence when water is added, but
+    that the R-double appears and persists for 200ns after the water makes its way
+    into the crystal. However, the authors also show that nonuniformly spaced
+    monomers can give rise to the R-Double feature, a seeming counterexample to the
+    necessity of water.  Is the R-double feature with water because the monomers
+    are now irregularly spaced? What happens when the waters are removed and the
+    scattering re-performed in Fig 17c(bottom)?}
     \end{quote}
@@
     spaced stacking. As soon as the restraints are released, R-double fades and the
-    monomer spacing becomes uniform. We modified the text on page _ in order to more
+    monomer spacing becomes uniform. We modified the text on page \_ in order to more
     clearly convey this message:
@@
     of R-double by stabilizing non-uniform spacing through hydrogen bonding, as the
-    reviewer suggests. We clarified the text on page _ in order to make this 
+    reviewer suggests. We clarified the text on page \_ in order to make this 
     conclusion clear:
@@
     gives way to reflections which are easily misinterpretted. We have added the
-    following text highlighted in red to the text shown on Page _ in order to
+    following text highlighted in red to the text shown on Page \_ in order to
     acknowledge that tail tilt is a valid explanation of R-spot-like reflections 
@@
     there will be some structural differences. There are many ways to tune a force
-    field in order to achieve this. We prefer to work with an "out-of-the-box"
-    force field since they are widely used and can be applied to vast number of
-    systems. The ultimate goal of our work is to create new monomers that can
-    achieve specfic separations.  If we can gain experimentally-consistent insights
-    using our model simulated with GAFF, then we can have increased confidence in
-    future predictions generated from systems built with unsynthesized monomers.
-    With that said, we think that it would be interesting to repeat our analysis
-    using different and/or optimized force fields in a future study in order to
-    comment on the signficance of any differences.
+    field in order to achieve this. As stated earlier, we prefer to work with an
+    "out-of-the-box" force field since they are widely used and can be applied to
+    vast number of systems. The ultimate goal of our work is to create new monomers
+    that can achieve specfic separations. If we can gain experimentally-consistent
+    insights using our model simulated with GAFF, then we can have increased
+    confidence in future predictions generated from systems built with
+    unsynthesized monomers.  With that said, we think that it would be interesting
+    to repeat our analysis using different and/or optimized force fields in a
+    future study in order to comment on the signficance of any differences.
 
-    %BJC: Emphasize main goal in intro (or pull a quote that says it)
-    %BJC: add justification of gaff to methods?
-    %BJC: Add force field optimization to future work
+    We have modified the paragraph of our conclusion which describes future
+    work (page \_) in order to acknowledge the possibility that a more tuned force
+    field could influence our results:
+
+    Old text: ``Future work, based on what has been learned in this study, may
+    help further improve the structural agreement between experiment and
+    simulation"
+
+    New text: ``  Future work, based on what has been learned in this study,
+    may help further improve the structural agreement between experiment and
+    simulation and test the sensitivity of our current conclusions to a more
+    accurate structure."
 
@@
     We expect that the simulated diffraction pattern will have a gaussian shape.
-    This exact result is shown in the Figure S-thingy of the supporting information.
+    This exact result is shown in the Figure S-\_ of the supporting information.
     With improper treatment of the monoclinic geometry, the gaussian shape is

### 2018-11-19 Ben_Manuscripts/structure_paper/Final_Draft.tex
Text written

@@
   A molecular-level understanding of LLC polymer membrane structure, enabled by
-  molecular dynamics (MD) simulations, will enhance our understanding of the role
+  molecular dynamics (MD) simulations, will enhance our comprehension of the role
   of monomer structure in solute transport and provide guidelines to reduce the
   large chemical space available to design monomers for creation of
-  separation-specific membranes. It is important that we model the system with
-  a nanoscopic pore structure that is maximally consistent with experimental
-  data.
-
-  A molecular-level understanding of LLC polymer membrane structure, enabled by
-  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
-  chemical space available to design monomers for creation of separation-specific
-  membranes. Useful molecular-level modeling should incorporate a detailed
-  picture of the nanoscopic pore structure, which is crucial to understanding the
-  role of monomer structure in solute transport and membrane design.  Atomistic
-  MD simulations can provide the required level of detail (Figure
-  \ref{fig:detailed_pore}), assuming the force fields are sufficiently accurate.  With
-  such an atomistic model, we can directly observe molecular-level solute
-  transport and suggest governing mechanisms. We can also observe how the choice
-  of head group interacts with solutes of interest. In addition, we can
-  interchange counterions which may influence both the pore size and the strength
-  of the Donnan potential.
+  separation-specific membranes. It is important that we model the system with a
+  nanoscopic pore structure that is maximally consistent with experimental data
+  in order to approximate the chemical environment experienced by solutes in 
+  future transport studies. Atomistic MD simulations can provide the required
+  level of detail (Figure \ref{fig:detailed_pore}), assuming the force fields are
+  sufficiently accurate. With such an atomistic model, we can directly observe
+  molecular-level solute transport and suggest governing mechanisms. We can also
+  observe how the choice of head group interacts with solutes of interest. In
+  addition, we can interchange counterions which may influence both the pore size
+  and the strength of the Donnan potential.
+
+%  A molecular-level understanding of LLC polymer membrane structure, enabled by
+%  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
+%  chemical space available to design monomers for creation of separation-specific
+%  membranes. Useful molecular-level modeling should incorporate a detailed
+%  picture of the nanoscopic pore structure, which is crucial to understanding the
+%  role of monomer structure in solute transport and membrane design.  Atomistic
+%  MD simulations can provide the required level of detail (Figure
+%  \ref{fig:detailed_pore}), assuming the force fields are sufficiently accurate.  With
+%  such an atomistic model, we can directly observe molecular-level solute
+%  transport and suggest governing mechanisms. We can also observe how the choice
+%  of head group interacts with solutes of interest. In addition, we can
+%  interchange counterions which may influence both the pore size and the strength
+%  of the Donnan potential.
 
@@
   Na-GA3C11 using the Generalized AMBER Force Field (GAFF)
-  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006} 
-  provided with AmberTools16 \cite{case_ambertools16_2016}. We assigned atomic
-  charges using the am1bccsym method of \texttt{molcharge} shipped with QUACPAC
-  from Openeye Scientific Software. We ran all molecular dynamics simulations 
-  using GROMACS 2016 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
+  \cite{wang_development_2004} with the Antechamber package
+  \cite{wang_automatic_2006} provided with AmberTools16
+  \cite{case_ambertools16_2016}. We chose GAFF because it has been parameterized
+  for use with organic molecules. Although researchers have optimized force
+  fields, including GAFF (cite), for use with liquid crystals, they are often
+  tuned in order to reproduce one or more experimental observables. Since liquid
+  crystals exist in a wide range of shapes and sizes, including candidate
+  monomers which we may study, we chose to stick with a widely used force field.
+  If we can reproduce experimental trends using a single 'out-of-the-box' force
+  field, then there will be no need to complicate our studies with customized
+  parameter sets. We assigned atomic charges using the am1bccsym method of
+  \texttt{molcharge} shipped with QUACPAC from Openeye Scientific Software. We
+  ran all molecular dynamics simulations using GROMACS 2016
+  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
 
@@
 
-  \subsection{Atomistic structure of the pore columns}
+  \subsection{Atomistic structure of the pore columns}\label{section:pore_composition}
 
@@
   order to address Question~\ref{point:composition} posed in the Introduction,
-  and observe the differences, if any, between the different plausible equilibrated
-  configurations studied so far. In general, the composition of each region, particularly within our
-  definition of the pore region, is similar between all systems. This suggests
-  that the details of transport may be relatively independent of the structural
-  differences between different possible structures studied here.
+  and observe the differences, if any, between the different plausible
+  equilibrated configurations studied so far. In general, the composition of each
+  region, particularly within our definition of the pore region, is similar
+  between all systems.
+
+%  This suggests that the details of transport may be
+%  relatively independent of the structural differences between different possible
+%  structures studied here.
 
   We plotted the number densities of heavy atoms in the head group
-  (Figure~\ref{fig:head_groups_regional_density}), carbon atoms in the tail region 
-  (Figure~\ref{fig:tails_regional_density}) and all sodium ions 
-  (Figure~\ref{fig:sodium_regional_density}). For the head group region, we used heavy
-  atoms making up the aromatic rings and carboxylate groups. For the tail region, we
-  used carbon atoms of the monomer tails (See Figure \ref{S-fig:monomer_color_coded}
-  of the SI for a diagram). We averaged the histograms over the equilibrated
-  portion of the trajectory. 
-  There is a gradient in pore composition transitioning radially from the hydrophilic 
-  to the hydrophobic region, rather than an abrupt division. Based on size-exclusion 
-  experiments, the pore radius was estimated to be 0.6 nm~\cite{zhou_supported_2005}. 
-  However, the simulations do not confine
-  sodium ions and head groups to just within this experimentally-defined pore region. For dry systems,
-  19\% of sodium ions exist outside the pore region (except sandwiched, ordered basin,
-  where 16\% are outside the pore). Additionally, in all cases, about 
-  3\% of the plotted tail density is located within the pore region (except ordered sandwiched,
-  where 1.5\% are within the pore region). For the solvated system, the results are similar,
-  however the head group density is shifted slightly radially outward, due to
-  swelling of the pore by water.
+  (Figure~\ref{fig:head_groups_regional_density}), carbon atoms in the tail
+  region (Figure~\ref{fig:tails_regional_density}) and all sodium ions
+  (Figure~\ref{fig:sodium_regional_density}). For the head group region, we used
+  heavy atoms making up the aromatic rings and carboxylate groups. For the tail
+  region, we used carbon atoms of the monomer tails (See Figure
+  \ref{S-fig:monomer_color_coded} of the SI for a diagram). We averaged the
+  histograms over the equilibrated portion of the trajectory.  There is a
+  gradient in pore composition transitioning radially from the hydrophilic to the
+  hydrophobic region, rather than an abrupt division. Based on size-exclusion
+  experiments, the pore radius was estimated to be 0.6
+  nm~\cite{zhou_supported_2005}.  However, the simulations do not confine sodium
+  ions and head groups to just within this experimentally-defined pore region.
+  For dry systems, 19\% of sodium ions exist outside the pore region (except
+  sandwiched, ordered basin, where 16\% are outside the pore). Additionally, in
+  all cases, about 3\% of the plotted tail density is located within the pore
+  region (except ordered sandwiched, where 1.5\% are within the pore region). For
+  the solvated system, the results are similar, however the head group density is
+  shifted slightly radially outward, due to swelling of the pore by water.
 
@@
   \end{figure}
+
+  \label{addition:pore_composition}
+  Our observations suggest that the details of transport may be relatively
+  independent of the structural differences between different possible structures
+  studied here. Despite the structural intricacies that give rive to differences
+  between the various metastable basins, all pores are characterized by dense,
+  primarily hydrophilic cores with a gradient towards a primarily hydrophobic
+  tail region far from the pore center. This implies that we might see the same
+  trends in transport properties from any of the systems studied so far. Since
+  the ultimate goal of our work is to design new monomers using high throughput
+  simulations, achieving that goal becomes tractable without the need to optimize
+  every system with an experimental dataset.
 
@@
 
-  We characterized the environment centered around the membrane pores and
-  learned that the pores are generally filled with monomer head groups and sodium
-  ions. All dry systems studied showed a similar distribution of sodium, head
-  groups and tails while the wet system shows evidence of slight swelling, with
-  minor changes in the distributions due to the presence of water molecules. We
-  also observed that there is not a hard partition between hydrophilic and
-  hydrophobic regions; instead, there is a gradient of chemical constituents. This finding raises
-  questions about the nature of size-exclusion separations in systems without a
-  well-defined pore size, which potentially could enable separations that
-  vary with chemical identity as well as size.
-
-%  We learned that we do not need water to create well-defined pore structures.
-%  Systems whose pores were filled with varying amounts of water showed a decrease
-%  in structuring relative to dry systems. At higher water concentrations, the pores
-%  begin to swell, which may be more conducive to transport.
+% BJC: new text
+  Although exactly reproducing the experimental 2D-WAXS pattern required
+  attention to minute structural details, we found that all systems showed
+  similar radial distribution functions characterized by a gradual radial
+  transition from a dense hydrophlic core to hydrophobic tails. This observation
+  enables us to study new systems that have not been experimentally characterized
+  with the expectation that any additional structural optimization will not
+  greatly influence trends in transport property predictions. The compositional
+  gradient itself raises questions about the nature of size-exclusion separations
+  in systems without well-defined pore boundaries, which potentially could enable
+  separations that vary with chemical identity as well as size.
+
+% BJC: old text:
+%  We characterized the environment centered around the membrane pores and
+%  learned that the pores are generally filled with monomer head groups and sodium
+%  ions. All dry systems studied showed a similar distribution of sodium, head
+%  groups and tails while the wet system shows evidence of slight swelling, with
+%  minor changes in the distributions due to the presence of water molecules. We
+%  also observed that there is not a hard partition between hydrophilic and
+%  hydrophobic regions; instead, there is a gradient of chemical constituents. This finding raises
+%  questions about the nature of size-exclusion separations in systems without a
+%  well-defined pore size, which potentially could enable separations that
+%  vary with chemical identity as well as size.
 
@@
   Future work, based on what has been learned in this study, may help further
-  improve the structural agreement between experiment and simulation. 
+  improve the structural agreement between experiment and simulation and test
+  the sensitivity of our current conclusions to a more accurate structure. 
   Polarizable force fields explicitly including $\pi-\pi$ interactions may be

### 2018-11-19 Ben_Manuscripts/structure_paper/response_to_reviewers.tex
Complete draft of response to reviewers

@@
 \usepackage{xr}
+\usepackage{xcolor}
+\usepackage{siunitx}
+\usepackage{gensymb}
 
@@
 
-    Author reply: We thank the reviewer for their constructive feedback and aim to address all of their concerns.
+    Author reply: We thank the reviewer for their constructive feedback and aim to 
+    address all of their concerns.
 
@@
 	    time, the authors make arguments including (1) pores are made from five columns
-	    of monomers, (2) that water is present in the "dry" structures, and (3) that a
+	    of monomers, (2) that water is present in the ``dry" structures, and (3) that a
 	    scattering feature comes from tail packing, not tilt: These observations
@@
     the purpose of our study, as it is important that we properly convey our
-    message. The main purpose our work is to give a detailed description of the
+    message. The main purpose of our work is to give a detailed description of the
     structure of a lyotropic liquid crystal membrane backed by experimental data.
@@
     possible. To clarify this purpose, we have modified and added text to the
-    paragraph on page \_ of the introduction, in which we state our perceived
-    importance of knowing the most experimentally-consistent structure:
+    paragraph on page~\pageref{M-rework:purpose} of the introduction, in which we
+    state our perceived importance of knowing the most experimentally-consistent
+    structure:
 
@@
     are no catch-all force fields built for liquid crystal systems. We are interested in
-    what information we can gain from a widely-used out-of-the-box force field and in future
+    what information we can gain from a widely-used `out-of-the-box' force field and in future
     work, we will validate whether GAFF is sufficient for reproducing trends in
     experimental separation properties. To clarify our use of GAFF, we have added
-    the following text to Secton~\ref{method:parameterization} of the Methods on
-    page ~\pageref{method:parameterization}.
+    the following text to Secton~\ref{M-method:parameterization} of the Methods on
+    page~\pageref{M-method:parameterization}.
 
@@
     organic molecules. Although researchers have optimized force fields, including
-    GAFF (cite), for use with liquid crystals, they are often tuned in order to
-    reproduce one or more experimental observables. Since liquid crystals exist in
-    a wide range of shapes and sizes, including candidate monomers which we may
-    study, we chose to stick with a widely used force field. If we
-    can reproduce experimental trends using a single 'out-of-the-box' force field,
-    then there will be no need to complicate our studies with customized parameter
-    sets."
+    GAFF, for use with liquid crystals, they are often tuned in order to
+    reproduce one or more experimental observables for specific types of liquid 
+    crystal molecules.$^{29,30}$ Since liquid crystals exist in a wide range of shapes and
+    sizes, including candidate monomers which we may study, we chose to stick with
+    a widely used force field. If we can reproduce experimental trends using a 
+    single `out-of-the-box' force field, then there will be no need to complicate
+    our studies with customized parameter sets."
 
-    We have added the following citation:
-    %cite1: liquid crystal gaff tuned to get phase transition temperature.
+    We have added the following citations:
+    \begin{itemize}
+    \item Cook, M. J.; Wilson, M. R. Development of an All-Atom Force Field for the Simulation
+    of Liquid Crystal Molecules in Condensed Phases (LCFF). Mol. Cryst. Liq. Cryst.
+    2001, 357, 149–165.
+    \item Boyd, N. J.; Wilson, M. R. Optimization of the Gaff Force Field to Describe Liquid
+    Crystal Molecules: The Path to a Dramatic Improvement in Transition Temperature
+    Predictions. Phys. Chem. Chem. Phys. 2015, 17, 24851–24865.
+    \end{itemize}
 
@@
     been undersold in the original draft of the manuscript. We have added the
-    following concluding paragraph the end of
-    Section~\label{section:pore_composition} on
-    page~\pageref{addition:pore_composition} in order to drive the point home:
+    following concluding paragraph to the end of
+    Section~\ref{M-section:pore_composition} on
+    page~\pageref{M-addition:pore_composition} in order to drive the point home:
 
@@
 
-    We also modified a paragraph in our conclusion on page \_ to better
-    emphasize our point:
+    We also modified a paragraph in our conclusion on page~\pageref{M-rework:conclusion}
+    to better emphasize our point:
 
@@
 
-    \end{quote}
-
     \item \begin{quote}
@@
     6 column-per-pore system with experimental pore spacing. As mentioned in the
-    text, the vertical stacking distance between monomers in that system is far too
-    large. The columns are `stretched' in the $z$-direction allowing the pores take
-    up less space on the $xy$ plane and thus pack closer together.
+    text on page~\pageref{M-6colperpore}, the vertical stacking distance between 
+    monomers in that system is far too large. The columns are `stretched' in the
+    $z$-direction allowing the pores take up less space on the $xy$ plane and 
+    thus pack closer together.
 
@@
     number of columns-per-pore influences the pore radius which is important for
-    determining the limits of size-exclusion-based separations. It also tells use
+    determining the limits of size-exclusion-based separations. It also tells us
     the density of interacting sites within the pore which may play a role in small
     molecule transport. We have added the following text to the main document at
-    the end of Section~\ref{M-section:mon_per_pore} on page \_:
+    the end of Section~\ref{M-section:mon_per_pore} on page~\pageref{M-addition:pore_radius}:
 
@@
     monomer head groups.  The pore radius increases with the number of columns per
-    pore (See Figure~\ref{S-fig:pore_radius}.  This radius is likely related to the
-    size of the molecules which can be excluded by this type of membrane. We may be
+    pore (See Figure~\ref{S-fig:pore_radius}). This radius is likely related to the
+    size of the molecules which can be excluded by this type of membrane. One may be
     able to control LLC membrane pore size by selecting monomers that are stable in
     configurations with more columns-per-pore."
+
+    We are unable to definitively answer the question of whether the 5-column 
+    structures are most likely to assemble in solution phase. The system does
+    not self-assemble on a timescale reasonable for simulation. See 
+    Section~\ref{S-section:self_assembly} of the supporting information where
+    we attempted self-assembly. These sorts of predictions are left for 
+    a separate effort that will use coarse grain models.
 
@@
     spaced stacking. As soon as the restraints are released, R-double fades and the
-    monomer spacing becomes uniform. We modified the text on page \_ in order to more
-    clearly convey this message:
+    monomer spacing becomes uniform. We modified the text on page~\pageref{M-modification:rdouble}
+    in order to more clearly convey this message:
 
@@
     than 3.7~\AA~apart, with COMs that are spaced 7.4 \AA~ from neighboring pairs
-    of monomers (Figure~\ref{fig:staggered_rzplot_norestraints}).  Our force field
+    of monomers (Figure~\ref{M-fig:staggered_rzplot_norestraints}). Our force field
     causes our system to tend towards uniformly spaced layers. Simulations of
@@
     studies of stacked $\pi-\pi$ systems that such uneven stacking could be
-    energetically stable.~\cite{tauer_beyond_2005}"
+    energetically stable.$^{52}$%.~\cite{tauer_beyond_2005}"
 
-    New text: ``We can also produce R-double if the LLC monomers are not
+    Modified text: ``We can also produce R-double if the LLC monomers are not
     uniformly spaced in the $z$-direction, but instead are placed in pairs that
     stack less than 3.7~\AA~apart, with COMs that are spaced 7.4 \AA~ from
-    neighboring pairs of monomers (Figure~\ref{fig:staggered_rzplot_norestraints}).
+    neighboring pairs of monomers (Figure~\ref{M-fig:staggered_rzplot_norestraints}).
     Simulations of unevenly spaced systems are only stable while position
@@
     evidence from quantum mechanical studies of stacked $\pi-\pi$ systems that such
-    uneven stacking could be energetically stable.~\cite{tauer_beyond_2005} As soon
+    uneven stacking could be energetically stable.$^{52}$ As soon %~\cite{tauer_beyond_2005} As soon
     as we remove position restraints, our system to tends towards uniformly spaced
@@
     of R-double by stabilizing non-uniform spacing through hydrogen bonding, as the
-    reviewer suggests. We clarified the text on page \_ in order to make this 
-    conclusion clear:
+    reviewer suggests. We clarified the text on page~\pageref{M-modification:rdouble2}
+    in order to make this conclusion clear:
 
@@
     with a shared water molecule, the monomers are drawn closer together (as
-    illustrated in Figure~\ref{fig:hbond_visualization}), which creates an
+    illustrated in Figure~\ref{M-fig:hbond_visualization}), which creates an
     asymmetry that allows R-double to appear. If a monomer head group shares a
@@
     (much like the configuration in
-     Figure~\ref{fig:staggered_rzplot_norestraints}). There are a modest number of
+     Figure~\ref{M-fig:staggered_rzplot_norestraints}). There are a modest number of
     occurrences of this scenario, which we quantify in further detail in the SI,
@@
     non-uniform stacking of head groups much like that shown in
-    Figure~\ref{fig:staggered_rzplot_norestraints}. When two vertically stacked
+    Figure~\ref{M-fig:staggered_rzplot_norestraints}. When two vertically stacked
     monomer head groups hydrogen bond with a shared water molecule, the monomers
     are drawn closer together (as illustrated in
-    Figure~\ref{fig:hbond_visualization}), which creates the asymmetry that allows
+    Figure~\ref{M-fig:hbond_visualization}), which creates the asymmetry that allows
     R-double to appear. If a monomer head group shares a hydrogen-bonded water
@@
     not give rise to R-double. We've added the resulting simulated XRD pattern to
-    the Supporting Information, Figure~\ref{S-TBD}.
+    the Supporting Information, Figure~\ref{S-fig:rdouble_water_removed}.
 
     \item \begin{quote}
-    \textit{3. The authors make the case that the R-spots feature comes from the structure of the hexagonal
-    tails, not their tilt. The authors should perform the scattering analysis to check if the R-spots are
-    present on the tilted-tails they constrain: This quick experiment would nail down their interpretation
-    here, or show that the tilted tails are also plausible (but not observed in this model).}
+    \textit{3. The authors make the case that the R-spots feature comes from the 
+    structure of the hexagonal tails, not their tilt. The authors should perform the
+    scattering analysis to check if the R-spots are present on the tilted-tails they
+    constrain: This quick experiment would nail down their interpretation here, or 
+    show that the tilted tails are also plausible (but not observed in this model).}
     \end{quote}
@@
     hexagonally in the tilted configuration which would independently give rise to
-    R-spots. Second, it is necessary to impose high force constant (>1000 kJ mol
+    R-spots. Second, it is necessary to impose high force constant ($>$ 1000 kJ mol$^-1$
     nm$^{-2}$) position restraints in order to maintain a tilt angle close to that
@@
     gives way to reflections which are easily misinterpretted. We have added the
-    following text highlighted in red to the text shown on Page \_ in order to
-    acknowledge that tail tilt is a valid explanation of R-spot-like reflections 
-    and to offer a reason a molecular reason why our monomers in our system do not
-    tilt:
+    following text highlighted in red to the text shown on page~\pageref{M-addition:rspots} in order to
+    acknowledge that tail tilt is a valid explanation of R-spot-like reflections:
 
@@
     in this particular WAXS dataset as the result of tilted alkane
-    chains~\cite{feng_scalable_2014}. {\color{red} This explanation is not
+    chains $^{16}$. {\color{red} This explanation is not  % feng_scalable_2014
     unfounded as there are examples in literature of systems where tilted liquid
-    crystals give rise to reflections that resemble R-spots (Cite, Cite).} We
-    measured the tilt angle of the alkane chains of the 280 K system by measuring
-    the angle made by the vector extending from top to bottom of each tail with
-    respect to the membrane plane.  We found that it equilibrates to an average
-    tilt angle of -2 $\pm$ 13\degree~(Figure~\ref{fig:tilt}), far from the
-    37\degree~tilt angle previously used to explain R-spots. Even when we placed
-    position restraints on the monomers in a tilted initial configuration, monomers
-    quickly reduced their tilt relative to the $xy$ plane to an angle statisically
-    indistinguishable from zero (see Section \ref{S-section:tail_tilt} of the SI).
-    {\color{red} While it is plausible that our force field may in part be
-    responsible for the tendency of monomers to stay nearly flat, the monomer tails
-    lack the functional groups which are known to facilitate tail tilting (cite).}"
+    crystals give rise to reflections that resemble R-spots.$^{45,46}$} We
+    measured the tilt angle of the alkane chains ..."
+
+    We have added the following citations in support of the above statement:
+    \begin{itemize}
+
+    \item Percec, V.; Imam, M. R.; Peterca, M.; Wilson, D. A.; Graf, R.; Spiess, H. W.; Balagu-
+    rusamy, V. S. K.; Heiney, P. A. Self-Assembly of Dendronized Triphenylenes into Helical
+    Pyramidal Columns and Chiral Spheres. J. Am. Chem. Soc. 2009, 131, 7662–7677.
+
+    \item Gearba, R. I.; Anokhin, D. V.; Bondar, A. I.; Bras, W.; Jahr, M.; Lehmann, M.;
+    Ivanov, D. A. Homeotropic Alignment of Columnar Liquid Crystals in Open Films by
+    Means of Surface Nanopatterning. Adv. Mater. 2007, 19, 815–820.
+
+    \end{itemize}
 
@@
     case. It is common for researchers to run simulations for an insufficient
-    length of time and to make bold claims. We acknowledge the shortcomings of our
+    length of time and to make bold claims. While we feel that we have run our 
+    simulations sufficiently long, we still acknowledge the shortcomings of our
     techniques in order to inspire other researchers to build on our initial work.
@@
     field in order to achieve this. As stated earlier, we prefer to work with an
-    "out-of-the-box" force field since they are widely used and can be applied to
+    `out-of-the-box' force field since they are widely used and can be applied to
     vast number of systems. The ultimate goal of our work is to create new monomers
@@
     We have modified the paragraph of our conclusion which describes future
-    work (page \_) in order to acknowledge the possibility that a more tuned force
-    field could influence our results:
+    work (page~\pageref{M-addition:forcefield-structure}) in order to acknowledge
+    the possibility that a more tuned force field could influence our results:
 
@@
 
-    New text: ``  Future work, based on what has been learned in this study,
+    New text: ``Future work, based on what has been learned in this study,
     may help further improve the structural agreement between experiment and
@@
     We expect that the simulated diffraction pattern will have a gaussian shape.
-    This exact result is shown in the Figure S-\_ of the supporting information.
+    This exact result is shown in the Figure~\ref{S-fig:xrd_noise} of the SI.
     With improper treatment of the monoclinic geometry, the gaussian shape is
@@
     \texttt{llcsim} repository which can be accessed at
-    \texttt{https://github.com/bencoscia/llcsim/blob/master/analysis/hexagonal\_packing.py}.
-
-    % Add code and clarify main text
+    \texttt{llcsim/analysis/hexagonal\_packing.py}.
+    Additionally, we have added an entry to Table~\ref{S-table:python_scripts} in 
+    order to make it clear where the code can be found.
 
@@
 
+	Author reply: We thank the reviewer for bringing up a good point. There are few studies
+	with experimental comparisons of sodium ion conduction. Conduction of pottasium in 
+	ion channels is quite common. The ionic conductivity is directly related to the 
+	diffusivity of the ion of interest, so if the dynamics of sodium are overpredicted
+	in our model, this could give rise to the discrepancy between experiment and simulation.
+	The diffusivity of sodium ions has been overpredicted with multiple models, including AMBER
+	where the diffusivity is about 2x too high. We have modified the text on page
+	\pageref{M-modification:conductivity} to include additional reasoning for the 
+	discrepancy between the simulated and experimental ionic conductivity.
+
+	Old text: ``The calculated value of ionic conductivity is 5 times higher than experiment 
+    likely because we simulated infinitely long, aligned pores. The ionic conductivity 
+    measurement to which we are comparing was done with an \SI{80}{\micro\metre}-thick film, 
+    nearly 10,000 times thicker than our simulated system. The thick film is likely 
+    imperfectly aligned and has defects leading to non-contiguous pores. It has been shown
+    that there is a large dependence of ionic conductivity on the alignment of the pores.
+    The ionic conductivity of an isotropically aligned film is ca. 85 times lower than that
+    of the nearly aligned film to which we are comparing.$^{16}$ We 
+    hypothesize that a thin, perfectly aligned film would have a value of ionic conductivity
+    in closer agreement with our model."
+
+    Revised text: ``The calculated value of ionic conductivity is 5 times higher than
+    experiment likely because we simulated infinitely long, aligned pores {\color{red} and
+    because our model over-predicts the diffusivity of sodium}. The ionic conductivity 
+    measurement to which we are comparing was done with an \SI{80}{\micro\metre}-thick film, 
+    nearly 10,000 times thicker than our simulated system. The thick film is likely 
+    imperfectly aligned and has defects leading to non-contiguous pores. It has been shown
+    that there is a large dependence of ionic conductivity on the alignment of the pores.
+    The ionic conductivity of an isotropically aligned film is ca. 85 times lower than that
+    of the nearly aligned film to which we are comparing$^{16}$. 
+    {\color{red} Additionally, sodium ions parameterized with AMBER parameters exhibit bulk
+    water diffusion coefficients that are two times greater than experiment.$^{56}$ We cannot 
+    definitively say how this ratio changes in the confined LLC pore environment, but
+    it is likely that sodium diffuses faster in our system which contributes to a higher 
+    ionic conductivity than experiment.}"
+
+	% Amber parameters used for sodium
+	% most studies with conductivity look at potassium
+	% look at diffusivities
+
 	\item \begin{quote}
-    \textit{If the authors either (a) strengthen the cases for their proposed structural insights being  highly 
-    likely (not just plausible), or (b) make a stronger case for why these particular insights have important 
-    ramifications for our understanding of LLC's (their significance), then it would be easier to publish this 
-    immediately. This reviewer's opinion is that this work would find a broader interested audience with a more
-    concise focus on these physical insights, which could be accomplished by moving more content 
-    (e.g., dihedral correlations) to the SI.}
+    \textit{If the authors either (a) strengthen the cases for their proposed structural
+    insights being  highly likely (not just plausible), or (b) make a stronger case for
+    why these particular insights have important ramifications for our understanding of 
+    LLC's (their significance), then it would be easier to publish this immediately. This
+    reviewer's opinion is that this work would find a broader interested audience with a more
+    concise focus on these physical insights, which could be accomplished by moving more
+    content (e.g., dihedral correlations) to the SI.}
     \end{quote}
+
+    Author reply: We feel that the additions and modifications to the sections cited above 
+    have made the intent of our work clearer and helped communicate the significance of 
+    our learned insights for future work on this topic. We have clarified the purpose of work
+    and what we expect to learn from it. We have commented on the significance of knowing the
+    number of columns-per-pore. We have emphasized the observation that the radial distribution
+    of monomer components is relatively independent of the system's initial configuration
+    which is important for future high-throughput work. We have clarified and strengthened our
+    reasoning for the existence of the R-double feature.
+
+    We sympathize with the reviewer's desire for a more concise manuscript but feel that most 
+    of the information presented is necessary in order to come to a full understanding of the 
+    work we've performed (an opinion shared by Reviewer 2). As a compromise, we've made efforts 
+    to shorten the manuscript by moving figures and discussions which draw the reader's attention
+    from the important physical insights to the SI. Excluding additional citations (new citations
+    take up about a page in the new draft), we have reduced the total length of the manuscript 
+    by 3 pages (including any additions documented above). The following changes made this possible:
+
+    \begin{itemize}
+
+    \item We moved the plots of the 1D Correlation functions, $g(z)$, used to calculate 
+    correlation lengths from Section~\ref{M-section:rpi} to the SI, now Figure~\ref{S-fig:correlation}.
+    The most important information, the correlation lengths, is already presented in 
+    Table~\ref{M-table:correlation_length}.
+
+    \item We moved the discussion of the influence of system size on $g(z)$ 
+    from Section~\ref{M-section:rpi} to the Supporting Information, 
+    Section~\ref{S-section:correlation_functions}. We supplemented that discussion in
+    the main text with the following text:
+
+    ``We show that the system size in the $z$-direction does not significantly 
+    alter $g(z)$ in Section~\ref{S-section:correlation_functions} of the SI."
+
+    \item We removed the discussion of a system that we annealed from 500 K to 300 K
+    from Section~\ref{M-section:rpi} because it is described again (with better context)
+    in Section~\ref{M-section:slow_dynamics}.
+
+	\item We moved the discussion of a correlation function, $g(z)$, that averages
+	all slices of the 3D correlation function and the associated figure from 
+	Section~\ref{M-section:rpi} to Section~\ref{S-section:correlation_functions}.
+
+    \item We've supplemented the discussion of the influence of increased noise in the 
+    $z$-direction and in the $xy$ plane on the shape and intensity of R-$\pi$ with the
+    following paragraph:
+
+    ``We also used our simplified systems in order to study the influence of increased
+    disorder in each dimension. Increasing $z$-directional disorder reduces the
+    intensity of R-$\pi$ without changing the shape of its $q_r$ cross-section.
+    Increasing disorder on the $xy$ plane, somewhat counterintuitively, reduces
+    the FWHM of the $q_r$ cross-section of R-$\pi$ with an insignificant effect
+    on its intensity. We explain these points in more depth in 
+    Section~\ref{S-section:simplified_sf}."
+
+    The full discussion, with figures, has been moved from Section~\ref{M-section:rpi}
+    to Section~\ref{S-section:simplified_sf}. The subsection of Section~\ref{M-section:rpi}
+    starting on page~\pageref{M-section:rpi_xsection} of the main text now has a primary
+    focus on the relationship between R-$\pi$ and inter-column correlation.
+
+    \item We moved the plots of dihedral autocorrelation functions to the SI, 
+    Figure~\ref{S-fig:dihedral}.
+
+    \item We moved the figure associated with physical property changes after cross-linking
+    to the SI, Figure~\ref{S-fig:xlink}, since its main findings are summarized sufficiently
+    in the text.
+
+    \end{itemize}
 
@@
 
-    ``Polarizable force fields explicitly including $\pi-\pi$ interactions may be able to draw stacked
-    monomers closer together"
+    ``Polarizable force fields such as AMOEBA which explicitly including $\pi-\pi$ interactions
+    between aromatic functional groups may be able to draw stacked monomers closer together. 
+    $^{57-59}$"
+
+    We have added citations with relevant force field examples, including AMOEBA:
+
+    \begin{itemize}
+
+    \item Shi, Y.; Xia, Z.; Zhang, J.; Best, R.; Wu, C.; Ponder, J. W.; Ren, P. Polarizable Atomic
+    Multipole-Based AMOEBA Force Field for Proteins. J. Chem. Theory Comput. 2013,
+    9, 4046–4063.
+
+    \item Kaminski, G. A.; Stern, H. A.; Berne, B. J.; Friesner, R. A. Development of an Accu-
+    rate and Robust Polarizable Molecular Mechanics Force Field from ab Initio Quantum
+    Chemistry. J. Phys. Chem. A 2004, 108, 621–627.
+
+    \item Lopes, P. E. M.; Lamoureux, G.; Roux, B.; MacKerell, A. D. Polarizable Empirical
+    Force Field for Aromatic Compounds Based on the Classical Drude Oscillator. J. Phys.
+    Chem. B 2007, 111, 2873–2885.
+
+    \end{itemize}
 

### 2018-11-19 Ben_Manuscripts/structure_paper/Final_Draft.tex
Complete draft of response to reviewers

@@
 
-  % reworking paragraph
+  % BJC: reworked text
+  \label{rework:purpose}
   A molecular-level understanding of LLC polymer membrane structure, enabled by
@@
   for use with organic molecules. Although researchers have optimized force
-  fields, including GAFF (cite), for use with liquid crystals, they are often
-  tuned in order to reproduce one or more experimental observables. Since liquid
-  crystals exist in a wide range of shapes and sizes, including candidate
+  fields, including GAFF, for use with liquid crystals, they are often tuned in 
+  order to reproduce one or more experimental observables for specific types of
+  liquid crystal molecules~\cite{cook_development_2001,boyd_optimization_2015}.
+  Since liquid crystals exist in a wide range of shapes and sizes, including candidate
   monomers which we may study, we chose to stick with a widely used force field.
-  If we can reproduce experimental trends using a single 'out-of-the-box' force
+  If we can reproduce experimental trends using a single `out-of-the-box' force
   field, then there will be no need to complicate our studies with customized
@@
 
-  \subsubsection{\textit{Determining equilibration time}}\label{method:equil_time}
+  \subsubsection{\textit{Determining Equilibration Time}}\label{method:equil_time}
 
@@
 
-  \subsubsection{\textit{Calculation of pore spacing}}\label{method:pore_spacing}
+  \subsubsection{\textit{Calculation of Pore Spacing}}\label{method:pore_spacing}
 
@@
 
-  \subsubsection{\textit{Generation of simulated X-ray diffraction patterns}}\label{method:xrd}
+  \subsubsection{\textit{Generation of Simulated X-ray Diffraction Patterns}}\label{method:xrd}
 
@@
 
-  \subsubsection{\textit{Pair distribution functions and correlation length}}\label{section:correlation_length}
+  \subsubsection{\textit{Pair Distribution Functions and Correlation Length}}\label{section:correlation_length}
 
@@
 
-  \subsubsection{\textit{Radial distribution functions}}\label{method:rdfs}
+  \subsubsection{\textit{Radial Distribution Functions}}\label{method:rdfs}
 
@@
 
-  \subsection{\textit{Ionic conductivity calculations}}\label{method:ionic_conductivity}
+  \subsection{\textit{Ionic Conductivity Calculations}}\label{method:ionic_conductivity}
 
@@
 
-  \subsection{Density of monomers around pores}\label{section:mon_per_pore}
+  \subsection{Density of Monomers Around Pores}\label{section:mon_per_pore}
 
@@
 
+  \label{6colperpore}
   Systems built with 5 columns around each pore equilibrate to a pore spacing
@@
   %BJC: added.
+  \label{addition:pore_radius}
   The number of columns per pore dictates the density of interaction sites within
@@
   surely play a role in transport of molecules that have an affinity for the monomer
-  head groups. 
-  %We measured the pore radius as the average distance from the pore
-  %center to each head group COM. 
-  The pore radius increases with the number of 
-  columns per pore (See Figure~\ref{S-fig:pore_radius}. This radius is likely 
+  head groups. The pore radius increases with the number of 
+  columns per pore (See Figure~\ref{S-fig:pore_radius}). This radius is likely 
   related to the size of the molecules which can be excluded by this type of 
-  membrane. We may be able to control LLC membrane pore size by selecting monomers
+  membrane. One may be able to control LLC membrane pore size by selecting monomers
   that are stable in configurations with more columns-per-pore.
 
-  \subsection{Simulated XRD comparison to 2D-WAXS data}
+  \subsection{Simulated XRD Comparison to 2D-WAXS Data}
 
@@
 
-  \subsubsection{The location of R-alkanes}\label{section:ralkanes}
+  \subsubsection{The Location of R-alkanes}\label{section:ralkanes}
 
@@
   simulations. We reached this conclusion because alkane parameters in GAFF and
-  AMBER forcefields generally reproduce data
+  AMBER force fields generally reproduce data
   well.~\cite{wang_development_2004,caleman_force_2012}
@@
 
-  \subsubsection{The location and intensity of R-pores}\label{section:rpores}
+  \subsubsection{The Location and Intensity of R-pores}\label{section:rpores}
 
@@
 
-  \subsubsection{The origin of R-spots}\label{section:rspots}
+  \subsubsection{The Origin of R-spots}\label{section:rspots}
 
@@
 
+  \label{addition:rspots}
   Previous literature has attributed the R-spots reflection in this particular
@@
   systems where tilted liquid crystals give rise to reflections that resemble
-  R-spots (Cite, Cite). We measured the tilt angle of the alkane chains of the
-  280 K system by measuring the angle made by the vector extending from top to
+  R-spots~\cite{percec_self-assembly_2009,gearba_homeotropic_2007}. We 
+  measured the tilt angle of the alkane chains of the 280 K system by measuring
+  the angle made by the vector extending from top to
   bottom of each tail with respect to the membrane plane. We found that it
@@
   relative to the $xy$ plane to an angle statisically indistinguishable from zero
-  (see Section \ref{S-section:tail_tilt} of the SI). While it is plausible that 
-  our force field may in part be responsible for the tendency of monomers to stay
-  nearly flat, the monomer tails lack the functional groups which are known to
-  facilitate tail tilting.
+  (see Section \ref{S-section:tail_tilt} of the SI).
+
+  % There are other mechanism for tilt to occur so the following doesn't say much
+  %While it is plausible that 
+  %our force field may in part be responsible for the tendency of monomers to stay
+  %nearly flat, the monomer tails lack the functional groups which are known to
+  %facilitate tail tilting.
 
@@
 
-  \subsubsection{The position, shape, and intensity of R-$\pi$}\label{section:rpi}
+  \subsubsection{The Position, Shape, and Intensity of R-$\pi$}\label{section:rpi}
 
@@
 
-  \subsubsection*{Distance and correlation between stacked monomer head groups}
+  \subsubsection*{Distance and Correlation Between Stacked Monomer Head Groups}
 
@@
   distance between peaks corresponds to the average distance between stacked
-  monomer head groups (Figure~\ref{S-fig:correlation}). We calculated this
+  monomer head groups (Figure~\ref{S-fig:correlation}). We show that the system
+  size in the $z$-direction does not significantly alter $g(z)$ in 
+  Section~\ref{S-section:correlation_functions} of the SI. We calculated the
   equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between monomers
@@
   energetically favorable for the monomers to stack closer together
-  \cite{wang_development_2004}. It is also possible that the tails prevent
-  close stacking of monomer head groups and we do not achieve the timescales
-  necessary for them to rearrange into a necessarily more tightly packed
-  configuration. To test this chain-packing hypotheses, we equilibrated the
-  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
-  into a more tightly packed configuration. Before annealing and in order to
-  stabilize the hexagonal phase at 500 K, we placed harmonic restraints with
-  force constants of 1000 kJ mol$^{-1}$ nm$^{-2}$ between head group COMs within
-  each column as well as between head group COMs in adjacent columns. We saw no
-  improvement in packing distance over our 300 K models (see further discussion
-  in Section~\ref{section:slow_dynamics}).
-
-  %BJC: could move the following paragraph to supporting
-  The system size, in the $z$-direction, does not significantly alter $g(z)$.
-  In Figure~\ref{S-fig:correlation}, oscillations do not fully decay, so a taller
-  system may be necessary to fully capture the correlation function. We therefore
-  equilibrated a sandwiched system with twice as many monomers per column so that
-  the system size doubled in the $z$-direction. The correlation length increases
-  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
-  correlation functions are nearly identical and oscillatory behavior persists
-  throughout $g(z)$ in both cases (See
-  Figure \ref{S-fig:z_correlation_overlay}).
+  \cite{wang_development_2004}.
+
+% Moved to supporting
+%  It is also possible that the tails prevent
+%  close stacking of monomer head groups and we do not achieve the timescales
+%  necessary for them to rearrange into a necessarily more tightly packed
+%  configuration. We tested this hypothesis by annealing systems from high temperatures
+%  as outline in Section~\ref{S-chain_packing} of the SI but saw no improvement
+%  in packing distance.
+
+%  To test this chain-packing hypotheses, we equilibrated the
+%  system at 500 K and then annealed it to 300 K in an attempt to coerce the tails
+%  into a more tightly packed configuration. Before annealing and in order to
+%  stabilize the hexagonal phase at 500 K, we placed harmonic restraints with
+%  force constants of 1000 kJ mol$^{-1}$ nm$^{-2}$ between head group COMs within
+%  each column as well as between head group COMs in adjacent columns. We saw no
+%  improvement in packing distance over our 300 K models (see further discussion
+%  in Section~\ref{section:slow_dynamics}). 
+%  
+%  %BJC: could move the following paragraph to supporting
+%  The system size, in the $z$-direction, does not significantly alter $g(z)$.
+%  In Figure~\ref{S-fig:correlation}, oscillations do not fully decay, so a taller
+%  system may be necessary to fully capture the correlation function. We therefore
+%  equilibrated a sandwiched system with twice as many monomers per column so that
+%  the system size doubled in the $z$-direction. The correlation length increases
+%  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
+%  correlation functions are nearly identical and oscillatory behavior persists
+%  throughout $g(z)$ in both cases (See
+%  Figure \ref{S-fig:z_correlation_overlay}).
 
@@
 
-  \subsubsection*{Shape and Intensity of the $q_r$ cross-section of R-$\pi$}
+  \subsubsection*{Shape and Intensity of the $q_r$ Cross-section of R-$\pi$}\label{section:rpi_xsection}
 
@@
 
-  %BJC: I could move the following paragraph to supporting information since it
+  %BJC: Moved the following paragraph to supporting information since it
   % relies on a qualitative comparison between the following figure and the 
   % the original correlation functions which I moved to supporting already.
-  It therefore seems likely that the discrepancy between the shape and intensity of
-  R-$\pi$ generated from our simulations versus experiment is primarily due to
-  highly correlated columns in our highly symmetric initial configurations.
-  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
-  would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
-  average all $z$-slices of the 3D correlation function. Contributions to
-  $g(z)$ from head groups in other columns within the same pore, and with head
-  groups in different pores would cancel out. However, when we include all 
-  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
-  $z$-slices within 2.1~\AA~of the center of the correlation function 
-  (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
-  behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
-  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
-  reinforced by head groups in neighboring columns which is not expected
-  in a system where columns act independently.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.pdf}
-  \caption{When we average all $z$-slices of the 3D correlation function, the 
-  correlation length of the ordered sandwich configuration nearly triples compared 
-  to that shown in Figure~\ref{fig:z_correlation_sandwich}.}\label{fig:z_correlation_fullbox}
-  \end{figure}
+  % could come off as confusing unless you are really thinking about these systems.
+%  It therefore seems likely that the discrepancy between the shape and intensity of
+%  R-$\pi$ generated from our simulations versus experiment is primarily due to
+%  highly correlated columns in our highly symmetric initial configurations.
+%  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
+%  would very closely resemble Figure~\ref{S-fig:z_correlation_sandwich} when we 
+%  average all $z$-slices of the 3D correlation function. Contributions to
+%  $g(z)$ from head groups in other columns within the same pore, and with head
+%  groups in different pores would cancel out. However, when we include all 
+%  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
+%  $z$-slices within 2.1~\AA~of the center of the correlation function 
+%  (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
+%  behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
+%  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
+%  reinforced by head groups in neighboring columns which is not expected
+%  in a system where columns act independently.
+
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.pdf}
+%  \caption{When we average all $z$-slices of the 3D correlation function, the 
+%  correlation length of the ordered sandwich configuration nearly triples compared 
+%  to that shown in Figure~\ref{fig:z_correlation_sandwich}.}\label{fig:z_correlation_fullbox}
+%  \end{figure}
 
@@
 
-  \subsubsection*{Quenched disorder in ensembles of configurations}
+  \subsubsection*{Quenched Disorder in Ensembles of Configurations}
 
@@
 
-  \subsubsection*{The implications of the new-found understanding of R-$\pi$}
+  \subsubsection*{The Implications of the New-found Understanding of R-$\pi$}
 
@@
 
+  % modified
+  \label{modification:rdouble}
   We can also produce R-double if the LLC monomers are not uniformly spaced in
@@
 
+  \label{modification:rdouble2}
   The addition of a small amount of water to the pores stabilizes non-uniform
@@
 
-  \subsection{Atomistic structure of the pore columns}\label{section:pore_composition}
+  \subsection{Atomistic Structure of the Pore Columns}\label{section:pore_composition}
 
@@
 
-  \subsection{Slow dynamics}\label{section:slow_dynamics}
+  \subsection{Slow Dynamics}\label{section:slow_dynamics}
 
@@
 
-  The calculated value of ionic conductivity is 5 times higher than experiment likely because 
-  we simulated infinitely long, aligned pores. The ionic conductivity measurement 
+  \label{modification:conductivity}
+  The calculated value of ionic conductivity is 5 times higher than experiment 
+  likely because we simulated infinitely long, aligned pores and because our 
+  model over-predicts the diffusivity of sodium. The ionic conductivity measurement 
   to which we are comparing was done with an \SI{80}{\micro\metre}-thick film, 
@@
   isotropically aligned film is ca. 85 times lower than that of the nearly aligned
-  film to which we are comparing~\cite{feng_scalable_2014}. We hypothesize that a 
+  film to which we are comparing~\cite{feng_scalable_2014}. Additionally,
+  the parameters for sodium ions in this system exhibit bulk water diffusion 
+  coefficients that are two times greater than experiment ~\cite{bruce_molecular_2002}.
+  We cannot definitively say exactly how this ratio changes in the confined LLC pore
+  environment, but it is likely that sodium diffuses faster in our system which
+  contributes to a higher ionic conductivity than experiment.
+
+  We hypothesize that a 
   thin, perfectly aligned film would have a value of ionic conductivity in closer
@@
 
-  \subsection{Effect of cross-linking}\label{section:xlink}
+  \subsection{Effect of Cross-linking}\label{section:xlink}
 
@@
   There are only minor changes to the physical characteristics of these systems when 
-  they are cross-linked (See Figure~\ref{fig:xlink}). The ionic conductivity of 
+  they are cross-linked (See Figure~\ref{S-fig:xlink}). The ionic conductivity of 
   the sandwiched configuration decreases while that of the parallel displaced 
@@
 
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=\textwidth]{xlink_charts.pdf}
-  \caption{There are minor differences between the physical properties of a
-  crosslinked (xlink) system versus an uncrosslinked system. The sandwiched configuration (S)
-  exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)
-  configuration remains constant. The pore spacing of both systems decreases upon cross-linking.
-  The vertical distance between stacked monomers increases in the sandwiched configuration
-  and decreases in the parallel displaced configuration. The correlation length decreases
-  in both configurations.}\label{fig:xlink}
-  \end{figure}
+%  \begin{figure}[!htb]
+%  \centering
+%  \includegraphics[width=\textwidth]{xlink_charts.pdf}
+%  \caption{There are minor differences between the physical properties of a
+%  crosslinked (xlink) system versus an uncrosslinked system. The sandwiched configuration (S)
+%  exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)
+%  configuration remains constant. The pore spacing of both systems decreases upon cross-linking.
+%  The vertical distance between stacked monomers increases in the sandwiched configuration
+%  and decreases in the parallel displaced configuration. The correlation length decreases
+%  in both configurations.}\label{fig:xlink}
+%  \end{figure}
 
@@
 % BJC: new text
+  \label{rework:conclusion}
   Although exactly reproducing the experimental 2D-WAXS pattern required
@@
 
+  \label{addition:forcefield-structure}
   Future work, based on what has been learned in this study, may help further
@@
   the sensitivity of our current conclusions to a more accurate structure. 
-  Polarizable force fields explicitly including $\pi-\pi$ interactions may be
-  able to draw stacked monomers closer together 
+  Polarizable force fields such as AMOEBA which explicitly including $\pi-\pi$ interactions
+  between aromatic functional groups may be able to draw stacked monomers closer together 
   ~\cite{shi_polarizable_2013,kaminski_development_2004,lopes_polarizable_2007}. 

### 2018-11-19 Ben_Manuscripts/structure_paper/supporting_information.tex
Complete draft of response to reviewers

@@
   \bibliographystyle{ieeetr}
-  \graphicspath{{./figures/supporting_figures/}}  % put all the figures here
+  %\graphicspath{{./figures/supporting_figures/}}  % put all the figures here
+  \graphicspath{{./figures/}}
   \maketitle
@@
   \\ \hline
+
+  \texttt{/analysis/hexagonal\_packing.py} & \ref{M-section:rspots} & Calculate Fourier transform of
+  2D array of hexagonal scatterers as shown in Figure~\ref{M-fig:hexagonal_ft} of the main text. \\ \hline
 
@@
 
+  \section{Pore radius as a function of monomers per column}\label{section:pore_radius}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{\linewidth}
+  \includegraphics[width=\textwidth]{pore_radius.pdf}
+  \end{subfigure}
+  \caption{The pore radius increases as we increase the number of columns per pore.}\label{fig:pore_radius}
+  \end{figure}
+
   \section{Noise in simulated diffraction patterns}\label{section:xrd_noise}
@@
 
-  \section{Correlation Functions}
+  \section{Correlation Functions}\label{section:correlation_functions}
 
@@
 	  monomers.}\label{fig:correlation}
+  \end{figure}
+
+  The system size, in the $z$-direction, does not significantly alter $g(z)$.
+  In Figure~\ref{S-fig:correlation}, oscillations do not fully decay, so a taller
+  system may be necessary to fully capture the correlation function. We therefore
+  equilibrated a sandwiched system with twice as many monomers per column so that
+  the system size doubled in the $z$-direction. The correlation length increases
+  modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA. However, visually, the
+  correlation functions are nearly identical and oscillatory behavior persists
+  throughout $g(z)$ in both cases (See Figure \ref{S-fig:z_correlation_overlay}).
+
+  It seems likely that the discrepancy between the shape and intensity of
+  R-$\pi$ generated from our simulations versus experiment is primarily due to
+  highly correlated columns in our highly symmetric initial configurations.
+  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
+  would very closely resemble Figure~\ref{S-fig:z_correlation_sandwich} when we 
+  average all $z$-slices of the 3D correlation function. Contributions to
+  $g(z)$ from head groups in other columns within the same pore, and with head
+  groups in different pores would cancel out. However, when we include all 
+  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
+  $z$-slices within 2.1~\AA~of the center of the correlation function 
+  (see Section~\ref{M-section:correlation_length}), $g(z)$ shows oscillatory 
+  behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
+  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
+  reinforced by head groups in neighboring columns which is not expected
+  in a system where columns act independently.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.pdf}
+  \caption{When we average all $z$-slices of the 3D correlation function, the 
+  correlation length of the ordered sandwich configuration nearly triples compared 
+  to that shown in Figure~\ref{fig:z_correlation_sandwich}.}\label{fig:z_correlation_fullbox}
   \end{figure}
@@
   vertically stacked monomer pairs share hydrogen bonds with a common water molecule (See
-  Section~\ref{M-section:rdouble} of the main text). We quantified the occurence of
-  these pairing interactions by binning the $z$-positions of the center of mass of 
+  Section~\ref{M-section:rdouble} of the main text). It is not a consequence of the 
+  structure of water itself because R-double still persists if we removed water from 
+  the trajectory which gives rise to the feature (Figure~\ref{fig:rdouble_water_removed}). 
+  We quantified the occurence of pairing interactions by binning the $z$-positions of the center of mass of 
   the monomer head groups into 20 bins, the same number as the monomers per column. 
@@
   there is periodicity at twice the $\pi$-stacking distance.
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.45\textwidth]{water_removed_rdouble.png}
+  \caption{When water is removed from the trajectory which produces R-double,
+  R-double is still present since it is the result of uneven spacing between 
+  head groups.}\label{fig:rdouble_water_removed}
+  \end{figure}
 
@@
   \end{figure}
+
+  \clearpage
 
@@
   \clearpage
+
+  \section{Influence of Cross-linking on physical properties}\label{section:xlink_physical}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=\textwidth]{xlink_charts.pdf}
+  \caption{There are minor differences between the physical properties of a
+  crosslinked (xlink) system versus an uncrosslinked system. The sandwiched configuration (S)
+  exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)
+  configuration remains constant. The pore spacing of both systems decreases upon cross-linking.
+  The vertical distance between stacked monomers increases in the sandwiched configuration
+  and decreases in the parallel displaced configuration. The correlation length decreases
+  in both configurations.}\label{fig:xlink}
+  \end{figure}
+
+\clearpage
 \bibliography{llc}

### 2018-11-19 Ben_Manuscripts/structure_paper/Final_Draft.tex
Fixes to references

@@
   head groups and the ether oxygens which attach the tails to the head group 
-  (see Figure \ref{S-fig:dihedrals} of the SI). We exclude the dihedral from the middle tail 
+  (see Figure \ref{S-fig:dihedral} of the SI). We exclude the dihedral from the middle tail 
   since it is fundamentally different than the two symmetric outside tails. We 
@@
   isotropically aligned film is ca. 85 times lower than that of the nearly aligned
-  film to which we are comparing~\cite{feng_scalable_2014}. Additionally,
-  the parameters for sodium ions in this system exhibit bulk water diffusion 
-  coefficients that are two times greater than experiment ~\cite{bruce_molecular_2002}.
-  We cannot definitively say exactly how this ratio changes in the confined LLC pore
-  environment, but it is likely that sodium diffuses faster in our system which
-  contributes to a higher ionic conductivity than experiment.
-
-  We hypothesize that a 
-  thin, perfectly aligned film would have a value of ionic conductivity in closer
-  agreement with our model.
+  film to which we are comparing~\cite{feng_scalable_2014}. Additionally, sodium 
+  ions parameterized with AMBER parameters exhibit bulk water diffusion coefficients
+  that are two times greater than experiment\cite{bruce_molecular_2002}. We cannot
+  definitively say how this ratio changes in the confined LLC pore environment,
+  but it is likely that sodium diffuses faster than experiment in our system which
+  contributes to a higher ionic conductivity.
+
+%  We hypothesize that a 
+%  thin, perfectly aligned film would have a value of ionic conductivity in closer
+%  agreement with our model.
 

### 2018-11-19 Ben_Manuscripts/structure_paper/supporting_information.tex
Fixes to references

@@
   The system size, in the $z$-direction, does not significantly alter $g(z)$.
-  In Figure~\ref{S-fig:correlation}, oscillations do not fully decay, so a taller
+  In Figure~\ref{fig:correlation}, oscillations do not fully decay, so a taller
   system may be necessary to fully capture the correlation function. We therefore
@@
   correlation functions are nearly identical and oscillatory behavior persists
-  throughout $g(z)$ in both cases (See Figure \ref{S-fig:z_correlation_overlay}).
+  throughout $g(z)$ in both cases (See Figure \ref{fig:z_correlation_overlay}).
 
@@
   If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
-  would very closely resemble Figure~\ref{S-fig:z_correlation_sandwich} when we 
+  would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
   average all $z$-slices of the 3D correlation function. Contributions to
@@
   by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
-  the data in Figure~\ref{fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
+  the data in Figure~\ref{M-fig:sim_rsection_fit}, the FWHM of R-$\pi$ agrees well
   with experiment, meaning the quenched configuration contains about the right

### 2018-11-21 Ben_Manuscripts/structure_paper/response_to_reviewers.tex
Fixes to references
Comments on letter.

@@
 
-\title{Response to reviewers: Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
-\author{Benjamin J. Coscia \and Joseph Yelk \and Matthew A. Glaser \and Douglas L. Gin \and Xunda Feng \and Michael R. Shirts}
-
 \begin{document}
 
-\maketitle
+%MRS: making the title a bit smaller, removing date.
+\begin{center}
+\textbf{Response to reviewers: Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}: \\
+Authors: Benjamin J. Coscia, Joseph Yelk, Matthew A. Glaser, Douglas L. Gin, Xunda Feng, and Michael R. Shirts
+\end{center}
 
@@
     structure, enabled by molecular dynamics (MD) simulations, will enhance our
-    comprehension of the role of monomer structure in solute transport and provide
+    understanding of the role of monomer structure in solute transport and provide
     guidelines to reduce the large chemical space available to design monomers for
@@
     what information we can gain from a widely-used `out-of-the-box' force field and in future
-    work, we will validate whether GAFF is sufficient for reproducing trends in
-    experimental separation properties. To clarify our use of GAFF, we have added
+    work, 
+    %MRS: suggest reprhasing as below?XS
+    %we will validate whether GAFF is sufficient for reproducing trends in
+    %experimental separation properties. 
+    we will look at sensitivity of the structural results to force field parameters.
+    To clarify our use of GAFF, we have added
     the following text to Secton~\ref{M-method:parameterization} of the Methods on
@@
 
+    %MRS: suggest pointing out that the LLC's here are not really characteristic of 
+    %more commonly studied monomers, so using those LLC force fields isn't really possible.
     New text: ``We chose GAFF because it has been parameterized for use with
@@
     revealed in this study, one of our main conclusions is that regardless of which
-    system we study, the radial distribution of monomer components stays
+    system we study, 
+    %MRS: Not really regardless above, as we only checked systems that were roughly right.
+    the radial distribution of monomer components stays
     consistent. From this, we can hypothesize that we will extract similar
@@
     Author reply: We agree with the reviewer that 5 columns-per-core is more
-    plausible than 4 and that much longer simulations may provide further
+    plausible than 4 and that much longer simulations could provide further
     supporting evidence. However, there is very little motion on the hundreds of
-    nanoseconds timescale that we simulated which suggests that we will not gain
-    any significant new insight by extending our simulations into the microsecond
-    regime. It is not feasible for us to carry out these simulations as it would
-    consume our computational resources with little reward.
+    nanoseconds timescale that we simulated, which suggests that we will not gain
+    any significant new insight by extending our simulations into the single microsecond
+    regime. 
+    %MRS: tweaked.
+    %It is not feasible to carry out these simulations as it would
+    %consume our computational resources with little reward.
+    It is not feasible at the present time to push the simulations at least an order of magnitude longer.
     %BJC: The following might apply:
@@
     thus pack closer together.  
+    %MRS: for above: Could you propose a textual response to deal with the confusion?
 
@@
     uneven stacking could be energetically stable.$^{52}$ As soon %~\cite{tauer_beyond_2005} As soon
-    as we remove position restraints, our system to tends towards uniformly spaced
+    as we remove position restraints, our system immediately moves towards uniformly spaced
     monomers."
@@
 
+    %MRS: color is only used twice in this response, and it is not explained at the top 
+    % what it is supposed to indicate.  Either that should be clarified and it should be used consistently, 
+    or changes should be indicated in other ways.  
     Modified text: ``Previous literature has attributed the R-spots reflection
@@
     field in order to achieve this. As stated earlier, we prefer to work with an
-    `out-of-the-box' force field since they are widely used and can be applied to
-    vast number of systems. The ultimate goal of our work is to create new monomers
+    `out-of-the-box' force field since they are widely used and can be applied 
+    %to vast 
+    transferably to a large 
+    number of systems. The ultimate goal of our work is to create new monomers
     that can achieve specfic separations. If we can gain experimentally-consistent
@@
     our mistake. The referenced GitHub repository was set to private due to
-    miscommunication with our collaborators but it has now been made public. Please
-    feel free to read through the code. We have performed checks to ensure that the
+    miscommunication with our collaborators but it has now been made public. 
+    %MRS: not needed.
+    %Please feel free to read through the code. 
+    We have performed checks to ensure that the
+    %MRS: can you be more specific what is meant by ``works properly''?
     code works properly, especially when simulating monoclinic unit cells. For
@@
     of configurations of randomly placed point scatterers in a monoclinic unit cell.
-    We expect that the simulated diffraction pattern will have a gaussian shape.
+    %MRS: tweak below.
+    %We expect that the simulated diffraction pattern will have a Gaussian shape.
+    In this case, the simulated diffraction pattern will be Gaussian.
     This exact result is shown in the Figure~\ref{S-fig:xrd_noise} of the SI.
@@
 	in our model, this could give rise to the discrepancy between experiment and simulation.
+%MRS: clarify diffusion in water. 
 	The diffusivity of sodium ions has been overpredicted with multiple models, including AMBER
@@
     have made the intent of our work clearer and helped communicate the significance of 
-    our learned insights for future work on this topic. We have clarified the purpose of work
+    our learned insights for future work on this topic. We have clarified the purpose of our work
     and what we expect to learn from it. We have commented on the significance of knowing the
@@
     of the information presented is necessary in order to come to a full understanding of the 
-    work we've performed (an opinion shared by Reviewer 2). As a compromise, we've made efforts 
-    to shorten the manuscript by moving figures and discussions which draw the reader's attention
-    from the important physical insights to the SI. Excluding additional citations (new citations
+    work we've performed (an opinion shared by Reviewer 2). 
+    %MRS: tweak
+    %As a compromise, we've made efforts to shorten the manuscript by 
+    We have attempted to satisfy both viewpoints, by carefully examining the manuscript for figures 
+    and discussions which draw the reader's attention from the important physical insights, and moving 
+    these to the SI. 
+    %MRS: could you clarify this?  Maybe just state how many pages were moved. 
+    Excluding additional citations (new citations
     take up about a page in the new draft), we have reduced the total length of the manuscript 
-    by 3 pages (including any additions documented above). The following changes made this possible:
-
+    by 3 pages (including any additions documented above). 
+    %MRS: tweak
+    %The following changes made this possible:
+    The following sections were moved to the SI, with only the key information left in the main paper:
     \begin{itemize}

### 2018-11-21 Ben_Manuscripts/structure_paper/response_to_reviewers.tex
Final reviewer response

@@
 appropriate revisions to the manuscript document. All changes to the text have
-been documented below.
+been documented below. In cases where we made major revisions, we included the
+original text (denoted by ``Original text:") followed by the new text (denoted by
+``New text:". If we only made additions or small changes to the existing text, 
+we highlighted them in red (denoted by ``Modified text:").
 
@@
     possible. To clarify this purpose, we have modified and added text to the
-    paragraph on page~\pageref{M-rework:purpose} of the introduction, in which we
-    state our perceived importance of knowing the most experimentally-consistent
-    structure:
+    paragraph at the end of page~\pageref{M-rework:purpose} of the introduction, 
+    in which we state our perceived importance of knowing the most 
+    experimentally-consistent structure:
 
-    Old text: ``A molecular-level understanding of LLC polymer membrane
+    Original text: ``A molecular-level understanding of LLC polymer membrane
     structure, enabled by molecular dynamics (MD) simulations, can provide
@@
 
-%This is unlikely to be achieved if one assembled these systems using
-%    united atom or coarse grained models due to the large number of potential
-%    metastable configurational basins which plague a system like ours which exhibts
-%    such slow dynamics.
-
     We do not intend for this study to be a validation of GAFF for this
@@
     what information we can gain from a widely-used `out-of-the-box' force field and in future
-    work, 
-    %MRS: suggest reprhasing as below?XS
-    %we will validate whether GAFF is sufficient for reproducing trends in
-    %experimental separation properties. 
-    we will look at sensitivity of the structural results to force field parameters.
-    To clarify our use of GAFF, we have added
-    the following text to Secton~\ref{M-method:parameterization} of the Methods on
+    work, we will look at sensitivity of the structural results to force field parameters.
+    To clarify our use of GAFF, we have added the following text to 
+    Secton~\ref{M-method:parameterization} of the Methods on
     page~\pageref{M-method:parameterization}.
 
-    %MRS: suggest pointing out that the LLC's here are not really characteristic of 
-    %more commonly studied monomers, so using those LLC force fields isn't really possible.
-    New text: ``We chose GAFF because it has been parameterized for use with
-    organic molecules. Although researchers have optimized force fields, including
-    GAFF, for use with liquid crystals, they are often tuned in order to
-    reproduce one or more experimental observables for specific types of liquid 
-    crystal molecules.$^{29,30}$ Since liquid crystals exist in a wide range of shapes and
-    sizes, including candidate monomers which we may study, we chose to stick with
-    a widely used force field. If we can reproduce experimental trends using a 
-    single `out-of-the-box' force field, then there will be no need to complicate
-    our studies with customized parameter sets."
+    Modified text: ``We parameterized the interaction potential for the liquid crystal
+    monomer Na-GA3C11 using the Generalized AMBER Force Field (GAFF) $^{26}$ with the
+    Antechamber package $^{27}$ provided with AmberTools16.$^{28}$ {\color{red} We 
+    chose GAFF because it has been parameterized for use with organic molecules. 
+    Although researchers have optimized force fields, including GAFF, for use with 
+    liquid crystals, they are often tuned in order to reproduce one or more experimental
+    observables for specific types of liquid crystal molecules.$^{29,30}$ Na-GA3C11
+    does not have a structure characteristic of more commonly studied liquid crystal
+    monomers so we chose to stick with a widely used force field. If we can reproduce
+    experimental trends using a single `out-of-the-box' force field, then there will 
+    be no need to complicate our studies with customized parameter sets.}
 
@@
     to use for comparison. Despite all of the structural intricacies which we have
-    revealed in this study, one of our main conclusions is that regardless of which
-    system we study, 
-    %MRS: Not really regardless above, as we only checked systems that were roughly right.
-    the radial distribution of monomer components stays
-    consistent. From this, we can hypothesize that we will extract similar
+    revealed in this study, one of our main conclusions is that for any of the 
+    systems we studied in this work, the radial distribution of monomer components
+    stays consistent. From this, we can hypothesize that we will extract similar
     transport results regardless of which configuration we use to conduct
@@
 
-    Old text: ``We characterized the environment centered around the membrane
+    Original text: ``We characterized the environment centered around the membrane
     pores and learned that the pores are generally filled with monomer head groups
@@
     any significant new insight by extending our simulations into the single microsecond
-    regime. 
-    %MRS: tweaked.
-    %It is not feasible to carry out these simulations as it would
-    %consume our computational resources with little reward.
-    It is not feasible at the present time to push the simulations at least an order of magnitude longer.
-    %BJC: The following might apply:
+    regime. It is not feasible at the present time to push the simulations at least
+    an order of magnitude longer.
+
     Some confusion may have been generated by agreement of the disordered basin
@@
     $z$-direction allowing the pores take up less space on the $xy$ plane and 
-    thus pack closer together.  
-    %MRS: for above: Could you propose a textual response to deal with the confusion?
+    thus pack closer together. We have modified the text starting at the very 
+    bottom of page~\pageref{M-6colperpore} for clarification:
+
+    Original text: ``Monomers in disordered basin systems built with 6 
+    columns-per-pore agree with experimental pore-to-pore distances within error, 
+    but stack too far apart. 6 column-per-pore disordered sandwiched and 
+    disordered parallel displaced configurations stack $\sim$~4.87 and 4.94 
+    \AA~apart respectively, which is $\sim$ 1.2~\AA~further apart than 
+    suggested by experiment."
+
+    New text: ``Monomers in disordered basins systems stack too far apart,
+    therefore they are not suitable candidate structures. Although their pore-to-pore
+    spacing is in close agreement with experiment, the 6 column-per-pore 
+    disordered sandwiched and disordered parallel displaced configurations 
+    stack $\sim$~4.87 and 4.94 \AA~apart respectively, which is $\sim$ 
+    1.2~\AA~further apart than suggested by experiment. The monomer columns
+    in these systems are effectively stretched in the $z$-direction which 
+    allows them and the pores to pack closer together on the $xy$ plane."
 
@@
     Author reply: We thank the reviewer for pushing us to provide more
-    significant physical insight based on the number of monomers per column. The
+    significant physical insight based on the number of columns-per-pore. The
     number of columns-per-pore influences the pore radius which is important for
@@
 
-    ``The number of columns per pore dictates the density of interaction sites
+    New text: ``The number of columns-per-pore dictates the density of interaction sites
     within each pore and the pore radius. A higher number of interaction sites will
@@
     spaced stacking. As soon as the restraints are released, R-double fades and the
-    monomer spacing becomes uniform. We modified the text on page~\pageref{M-modification:rdouble}
-    in order to more clearly convey this message:
+    monomer spacing becomes uniform. We modified the text in the first full 
+    paragraph of page~\pageref{M-modification:rdouble} in order to more clearly
+    convey this message:
 
-    Old text: ``We can also produce R-double if the LLC monomers are not
+    Original text: ``We can also produce R-double if the LLC monomers are not
     uniformly spaced in the $z$-direction, but instead form pairs that stack less
@@
 
-    Modified text: ``We can also produce R-double if the LLC monomers are not
+    New text: ``We can also produce R-double if the LLC monomers are not
     uniformly spaced in the $z$-direction, but instead are placed in pairs that
@@
 
-    Old text: ``When two vertically stacked monomer head groups hydrogen bond
+    Original text: ``When two vertically stacked monomer head groups hydrogen bond
     with a shared water molecule, the monomers are drawn closer together (as
@@
     hexagonally in the tilted configuration which would independently give rise to
-    R-spots. Second, it is necessary to impose high force constant ($>$ 1000 kJ mol$^-1$
+    R-spots. Second, it is necessary to impose high force constant ($>$ 1000 kJ mol$^{-1}$
     nm$^{-2}$) position restraints in order to maintain a tilt angle close to that
@@
     gives way to reflections which are easily misinterpretted. We have added the
-    following text highlighted in red to the text shown on page~\pageref{M-addition:rspots} in order to
-    acknowledge that tail tilt is a valid explanation of R-spot-like reflections:
+    following text, highlighted in red, to the text shown in the first full paragraph of
+    page~\pageref{M-addition:rspots} in order to acknowledge that tail tilt is a 
+    valid explanation of R-spot-like reflections:
 
-    %MRS: color is only used twice in this response, and it is not explained at the top 
-    % what it is supposed to indicate.  Either that should be clarified and it should be used consistently, 
-    or changes should be indicated in other ways.  
     Modified text: ``Previous literature has attributed the R-spots reflection
@@
     `out-of-the-box' force field since they are widely used and can be applied  
-    %to vast 
-    transferably to a large 
-    number of systems. The ultimate goal of our work is to create new monomers
-    that can achieve specfic separations. If we can gain experimentally-consistent
+    transferably to a large number of systems. The ultimate goal of our work is to create new monomers
+    that can achieve specific separations. If we can gain experimentally-consistent
     insights using our model simulated with GAFF, then we can have increased
@@
 
-    We have modified the paragraph of our conclusion which describes future
-    work (page~\pageref{M-addition:forcefield-structure}) in order to acknowledge
+    We have added to the paragraph (highlighted in red) of our conclusion which describes future
+    work (bottom of page~\pageref{M-addition:forcefield-structure}) in order to acknowledge
     the possibility that a more tuned force field could influence our results:
 
-    Old text: ``Future work, based on what has been learned in this study, may
+    Modified text: ``Future work, based on what has been learned in this study, may
     help further improve the structural agreement between experiment and
-    simulation"
-
-    New text: ``Future work, based on what has been learned in this study,
-    may help further improve the structural agreement between experiment and
-    simulation and test the sensitivity of our current conclusions to a more
-    accurate structure."
+    simulation {\color{red} and test the sensitivity of our current conclusions to a more
+    accurate structure.}"
 
@@
     miscommunication with our collaborators but it has now been made public. 
-    %MRS: not needed.
-    %Please feel free to read through the code. 
-    We have performed checks to ensure that the
-    %MRS: can you be more specific what is meant by ``works properly''?
-    code works properly, especially when simulating monoclinic unit cells. For
-    example, we generated test trajectories containing thousands of frames made up
-    of configurations of randomly placed point scatterers in a monoclinic unit cell.
-    %MRS: tweak below.
-    %We expect that the simulated diffraction pattern will have a Gaussian shape.
-    In this case, the simulated diffraction pattern will be Gaussian.
-    This exact result is shown in the Figure~\ref{S-fig:xrd_noise} of the SI.
-    With improper treatment of the monoclinic geometry, the gaussian shape is
-    skewed into an elliptical shape.
+    We have performed checks to ensure that the code properly handles monoclinic
+    unit cells. For example, we generated test trajectories containing thousands
+    of frames made up of configurations of randomly placed point scatterers in a
+    monoclinic unit cell. In this case, the simulated diffraction pattern will 
+    be Gaussian. This exact result is shown in the Figure~\ref{S-fig:xrd_noise}
+    of the SI. With improper treatment of the monoclinic geometry, the gaussian
+    shape is skewed into an elliptical shape.
 
@@
 	Author reply: We thank the reviewer for bringing up a good point. There are few studies
-	with experimental comparisons of sodium ion conduction. Conduction of pottasium in 
+	with experimental comparisons of sodium ion conduction. Conduction of potassium in 
 	ion channels is quite common. The ionic conductivity is directly related to the 
@@
 	in our model, this could give rise to the discrepancy between experiment and simulation.
-%MRS: clarify diffusion in water. 
-	The diffusivity of sodium ions has been overpredicted with multiple models, including AMBER
-	where the diffusivity is about 2x too high. We have modified the text on page
-	\pageref{M-modification:conductivity} to include additional reasoning for the 
-	discrepancy between the simulated and experimental ionic conductivity.
+	The diffusivity of sodium ions in water has been overpredicted with multiple models, 
+	including AMBER where the diffusivity is about 2x too high. We have modified the text 
+	on page 49 to include additional reasoning for the 
+	discrepancy between the simulated and experimental ionic conductivity:
 
-	Old text: ``The calculated value of ionic conductivity is 5 times higher than experiment 
-    likely because we simulated infinitely long, aligned pores. The ionic conductivity 
-    measurement to which we are comparing was done with an \SI{80}{\micro\metre}-thick film, 
-    nearly 10,000 times thicker than our simulated system. The thick film is likely 
-    imperfectly aligned and has defects leading to non-contiguous pores. It has been shown
-    that there is a large dependence of ionic conductivity on the alignment of the pores.
-    The ionic conductivity of an isotropically aligned film is ca. 85 times lower than that
-    of the nearly aligned film to which we are comparing.$^{16}$ We 
-    hypothesize that a thin, perfectly aligned film would have a value of ionic conductivity
-    in closer agreement with our model."
+%	Original text: ``The calculated value of ionic conductivity is 5 times higher than experiment 
+%    likely because we simulated infinitely long, aligned pores. The ionic conductivity 
+%    measurement to which we are comparing was done with an \SI{80}{\micro\metre}-thick film, 
+%    nearly 10,000 times thicker than our simulated system. The thick film is likely 
+%    imperfectly aligned and has defects leading to non-contiguous pores. It has been shown
+%    that there is a large dependence of ionic conductivity on the alignment of the pores.
+%    The ionic conductivity of an isotropically aligned film is ca. 85 times lower than that
+%    of the nearly aligned film to which we are comparing.$^{16}$ We 
+%    hypothesize that a thin, perfectly aligned film would have a value of ionic conductivity
+%    in closer agreement with our model."
 
-    Revised text: ``The calculated value of ionic conductivity is 5 times higher than
+    Modified text: ``The calculated value of ionic conductivity is 5 times higher than
     experiment likely because we simulated infinitely long, aligned pores {\color{red} and
@@
     of the information presented is necessary in order to come to a full understanding of the 
-    work we've performed (an opinion shared by Reviewer 2). 
-    %MRS: tweak
-    %As a compromise, we've made efforts to shorten the manuscript by 
-    We have attempted to satisfy both viewpoints, by carefully examining the manuscript for figures 
-    and discussions which draw the reader's attention from the important physical insights, and moving 
-    these to the SI. 
+    work we've performed (an opinion shared by Reviewer 2). We have attempted to satisfy both
+    viewpoints, by carefully examining the manuscript for figures and discussions which draw
+    the reader's attention from the important physical insights, and moving these to the SI. 
     %MRS: could you clarify this?  Maybe just state how many pages were moved. 
-    Excluding additional citations (new citations
-    take up about a page in the new draft), we have reduced the total length of the manuscript 
-    by 3 pages (including any additions documented above). 
-    %MRS: tweak
-    %The following changes made this possible:
-    The following sections were moved to the SI, with only the key information left in the main paper:
+    Including additions made above, we have reduced the total length of the body of the 
+    manuscript by 3 pages. The following sections were moved to the SI, with only the key
+    information left in the main paper:
     \begin{itemize}
@@
 
-    ``Polarizable force fields such as AMOEBA which explicitly including $\pi-\pi$ interactions
-    between aromatic functional groups may be able to draw stacked monomers closer together. 
-    $^{57-59}$"
+    Modified text: ``{\color{red} Polarizable} force fields {\color{red} such as AMOEBA which}
+    explicitly include $\pi-\pi$ interactions {\color{red} between aromatic functional groups}
+    may be able to draw stacked monomers closer together.{\color{red}$^{57-59}$}"
 

### 2018-11-21 Ben_Manuscripts/structure_paper/Final_Draft.tex
Final reviewer response

@@
   A molecular-level understanding of LLC polymer membrane structure, enabled by
-  molecular dynamics (MD) simulations, will enhance our comprehension of the role
+  molecular dynamics (MD) simulations, will enhance our understanding of the role
   of monomer structure in solute transport and provide guidelines to reduce the 
   large chemical space available to design monomers for creation of 
-  separation-specific membranes. It is important that we model the system with a
-  nanoscopic pore structure that is maximally consistent with experimental data
-  in order to approximate the chemical environment experienced by solutes in 
-  future transport studies. Atomistic MD simulations can provide the required
+  separation-specific membranes. It is important that we model the system with
+  a nanoscopic pore structure that is maximally consistent with experimental data
+  in order to best approximate the chemical environment experienced by solutes
+  in future simulated transport studies. Atomistic MD simulations can provide the required
   level of detail (Figure \ref{fig:detailed_pore}), assuming the force fields are
@@
   liquid crystal molecules~\cite{cook_development_2001,boyd_optimization_2015}.
-  Since liquid crystals exist in a wide range of shapes and sizes, including candidate
-  monomers which we may study, we chose to stick with a widely used force field.
+  Na-GA3C11 does not have a structure characteristic of more commonly studied 
+  liquid crystal monomers so we chose to stick with a widely used force field.
   If we can reproduce experimental trends using a single `out-of-the-box' force
@@
   stacked monomers, the $xy$ position of monomers with respect to vertically
-  adjacent monomers, and the number of columns per pore do influence the
+  adjacent monomers, and the number of columns-per-pore do influence the
   equilibrated structure and require further justification for their choices. We
@@
   head groups in the parallel displaced initial configuration stack with an offset
-  of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See Figure 
+  of $180^\circ/ncol$ where $ncol$ is the number of columns-per-pore. See Figure 
   \ref{S-fig:stacking} of the SI for a detailed illustration 
@@
 
-  The number of columns per pore is unknown, as stated in Question
+  The number of columns-per-pore is unknown, as stated in Question
   (\ref{point:monomernum}). We tested configurations constructed with a varied
-  number of columns per pore. We built systems in the sandwiched and parallel
-  displaced configurations with 4, 5, 6, 7 and 8 columns per pore.
+  number of columns-per-pore. We built systems in the sandwiched and parallel
+  displaced configurations with 4, 5, 6, 7 and 8 columns-per-pore.
 
@@
 
-  Our simulations best support a model built with 5 monomer columns per pore
+  Our simulations best support a model built with 5 monomer columns-per-pore
   based on the measured equilibrated pore-to-pore distances. To identify the
@@
   \ref{point:monomernum} in the introduction, we ran simulations of systems
-  created with 4--8 columns per pore. We built systems in both the parallel
+  created with 4--8 columns-per-pore. We built systems in both the parallel
   displaced and sandwiched configurations and equilibrated them according to the
@@
 	\includegraphics[width=\linewidth]{p2p.pdf}
-	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
+	\caption{Systems with 5 columns-per-pore have equilibrated pore spacings closest to
 			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
@@
   SAXS measurements (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4
-  columns per pore equilibrate to an average pore spacing 0.25 nm lower than
-  experiment. Ordered basin systems built with 6 columns per pore, have an
+  columns-per-pore equilibrate to an average pore spacing 0.25 nm lower than
+  experiment. Ordered basin systems built with 6 columns-per-pore, have an
   equilibrated pore spacing ca. 0.50 nm higher than experiment. Monomers in 
-  disordered basin systems built with 6 columns-per-pore agree with experimental
-  pore-to-pore distances within error, but stack too far apart. 6
-  column per pore disordered sandwiched and disordered parallel displaced
-  configurations stack $\sim$~4.87 and 4.94 \AA~apart respectively, which is
-  $\sim$ 1.2~\AA~further apart than suggested by experiment. 5 column-per-pore
-  systems stack, at a maximum, 0.9 \AA~further apart than experiment (see
-  Table~\ref{table:correlation_length}). The remainder of this discussion will
-  therefore focus on the analysis of systems built with 5 columns per pore.
+  disordered basins systems stack too far apart, therefore they are not 
+  suitable candidate structures. Although their pore-to-pore spacing is in
+  close agreement with experiment, the 6 column-per-pore disordered 
+  sandwiched and disordered parallel displaced configurations stack 
+  $\sim$~4.87 and 4.94 \AA~apart respectively, which is $\sim$ 
+  1.2~\AA~further apart than suggested by experiment. The monomer columns in
+  these systems are effectively stretched in the $z$-direction which allows
+  them and the pores to pack closer together on the $xy$ plane. 5 column-per-pore
+  systems stack, at a maximum, 0.9 \AA~further apart than experiment 
+  (see Table~\ref{table:correlation_length}). The remainder of this discussion
+  will therefore focus on the analysis of systems built with 5 columns-per-pore.
 
@@
   \label{addition:pore_radius}
-  The number of columns per pore dictates the density of interaction sites within
+  The number of columns-per-pore dictates the density of interaction sites within
   each pore and the pore radius. A higher number of interaction sites will 
@@
   head groups. The pore radius increases with the number of 
-  columns per pore (See Figure~\ref{S-fig:pore_radius}). This radius is likely 
+  columns-per-pore (See Figure~\ref{S-fig:pore_radius}). This radius is likely 
   related to the size of the molecules which can be excluded by this type of 
@@
   that are stable in configurations with more columns-per-pore.
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cccc}
+  \toprule
+  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
+  \midrule
+  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
+  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
+  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
+  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
+  Experiment         & --                 &    3.70                    & 9 $\pm$ 1               \\
+  \bottomrule
+  \end{tabular}
+  \caption{For 5 column-per-pore systems, the equilibrated vertical stacking distance, 
+  $\mathit{d}_{equil}$, of monomers in the disordered basin is approximately 0.6 \AA higher than
+  their initial configuration stacking distance, $\mathit{d}$, while $\mathit{d}_{equil}$ is 
+  smaller than $\mathit{d}$ for disordered basin systems, but 0.9 \AA higher than experiment. 
+  The correlation length is larger for systems in the ordered basin.}
+  \label{table:correlation_length}
+  \end{table}
 
@@
   addressing Question~\ref{point:xrdmatch} in the Introduction. We tested systems
-  built with 5 columns per pore in the parallel displaced and sandwiched
+  built with 5 columns-per-pore in the parallel displaced and sandwiched
   configurations at 300 K in the ordered and disordered basins, as those were the
@@
 
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{cccc}
-  \toprule
-  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
-  \midrule
-  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
-  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
-  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
-  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
-  Experiment         & --                 &    3.70                    & 9 $\pm$ 1               \\
-  \bottomrule
-  \end{tabular}
-  \caption{The correlation length is larger for systems in the ordered basin.
-	  The equilibrated vertical stacking distance, $\mathit{d}_{equil}$, is also
-	  smaller.}
-  \label{table:correlation_length}
-  \end{table}
-
   \subsubsection*{Shape and Intensity of the $q_r$ Cross-section of R-$\pi$}\label{section:rpi_xsection}
@@
   be energetically stable.~\cite{tauer_beyond_2005} As soon as we remove position
-  restraints, our system to tends towards uniformly spaced monomers.
+  restraints, our system immediately moves towards uniformly spaced monomers.
 
@@
   independent of the structural differences between different possible structures
-  studied here. Despite the structural intricacies that give rive to differences
+  studied here. Despite the structural intricacies that give rise to differences
   between the various metastable basins, all pores are characterized by dense, 
@@
   tail region far from the pore center. This implies that we might see the same
-  trends in transport properties from any of the systems studied so far. Since
-  the ultimate goal of our work is to design new monomers using high throughput
+  trends in transport properties from any of the systems studied so far. Since the
+  ultimate goal of our work is to design new monomers using high throughput 
   simulations, achieving that goal becomes tractable without the need to optimize
@@
   simulated 2D-XRD patterns, when we build our model in the ordered basin
-  parallel displaced configuration with 5 monomer columns per pore and 1 wt\%
+  parallel displaced configuration with 5 monomer columns-per-pore and 1 wt\%
   water. R-alkanes and R-pores appear where expected for the reasons originally
@@
   the sensitivity of our current conclusions to a more accurate structure. 
-  Polarizable force fields such as AMOEBA which explicitly including $\pi-\pi$ interactions
+  Polarizable force fields such as AMOEBA which explicitly include $\pi-\pi$ interactions
   between aromatic functional groups may be able to draw stacked monomers closer together 

### 2018-11-21 setup/equil.py

@@ -122,6 +122,16 @@ def simulate(mdp, top, config, out, restrained=False, mpi=False, np=4):
     p.wait()
 
 
+def check_energy(logname='em.log'):
+
+    with open('%s' % logname) as f:
+        for line in f:
+            if line.count("Potential Energy") == 1:
+                nrg = float(line.split()[3])
+
+    return nrg
+
+
 if __name__ == "__main__":
 
     args = initialize().parse_args()
@@ -138,11 +148,7 @@ if __name__ == "__main__":
 
     simulate('em.mdp', 'topol.top', '%s' % args.initial, 'em', mpi=args.mpi, np=args.nproc)
 
-    nrg = 1
-    with open('em.log') as f:
-        for line in f:
-            if line.count("Potential Energy") == 1:
-                nrg = float(line.split()[3])
+    nrg = check_energy(logname='em.log')
 
     # rebuild until energy minimization reaches a negative potential energy
     while nrg > 0:
@@ -152,10 +158,7 @@ if __name__ == "__main__":
 
         simulate('em.mdp', 'topol.top', '%s' % args.initial, 'em', mpi=args.mpi, np=args.nproc)
 
-        with open('em.log') as f:
-            for line in f:
-                if line.count("Potential Energy") == 1:
-                    nrg = float(line.split()[3])
+        nrg = check_energy(logname='em.log')
 
     simulate('nvt.mdp', 'topol.top', 'em.gro', 'nvt', mpi=args.mpi, np=args.nproc, restrained=True)
 
@@ -173,8 +176,11 @@ if __name__ == "__main__":
 
         copy = "cp nvt.gro %s.gro" % f
         p = subprocess.Popen(copy.split())
+        p.wait()
+
         copy = "cp nvt.trr %s.trr" % f
         p = subprocess.Popen(copy.split())
+        p.wait()
 
     generate_input_files(args.initial, 'npt', args.length_berendsen, genvel=False, barostat='berendsen')
     simulate('npt.mdp', 'topol.top', 'nvt.gro', 'berendsen', mpi=args.mpi, np=args.nproc)

### 2018-11-29 Ben_Manuscripts/transport/Outline.tex
Beginnings of outline for transport paper

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

\begin{document}
%  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section{Introduction}

  We need highly selective membranes in order to perform efficient separations.

  H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
  sized pores and have the potential to disrupt conventional membrane separation
  techniques by being selective based not only on size and charge, but on chemical
  functionality as well.

  We can only learn so much from experiment. MD can give us mechanistic insights with
  atomistic resolution so that we can intelligently design new membranes for 
  solute-specific separations.

  In previous work, we determined the most likely structure of the hexagonal phase 
  formed by the monomer Na-GA3C11.
  \begin{itemize}
  	\item We developed techniques for equilibrating the hexagonal phase made by
	neat monomer as well as with varying amounts of water in the pores.
  \end{itemize}

  In this work, we have determined the transport mechanisms and macroscopic transport 
  properties exhibited by a number of polar solutes with varying size, chemical 
  functionality and hydrophilic character.
  \begin{itemize}
	\item Many of the separations we are interested in involve polar organic 
	compounds.
  \end{itemize}

  We have compared our calculated diffusion coefficients with experimental measurements
  made using DOSY NMR.

  \section{Methods}

  \subsection{Molecular Dynamics Simulations}

  \subsubsection*{System Setup}

  There is a broad range of water concentrations which will form a stable 
  H\textsubscript{II} phase with Na-GA3C11. 
  \begin{itemize}
	\item In the literature this system is typically synthesized with close
	to 10 wt \% water
        \item However, Resel et al. noted that the system is likely fully 
	hydrated with less than 7 wt \% water.
	\item We decided to test two different levels of water content: 5 and 10 wt \%
  \end{itemize}

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

%  We equilibrated the initial configuration using the `wet' equilibration procedure
%  described in our previous work (reference to structure paper).
  %BJC: not sure I need to go into any details describing that procedure
%  \begin{itemize}
%	\item Series of NVT simulations with force constants on carbon atoms of aromatic
%	ring in head group
%	\item Force constants reduced according to the sequence: 1000000, 3162,
%	56, 8, 3, 2, 1, 0 kJ mol$^{-1}$ nm$^{-2}$ 
%  \end{itemize}

%  We cross-linked the equilibrated solvated configuration using the cross-linking procedure
%  described in our previous work.

  We equilibrated our initial configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work (reference to structure
	paper).
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimzation.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using long simulations, on the order of
	1 microsecond, with pressure controlled by the Parrinello-Rahman barostat.
  \end{itemize}

  \subsubsection*{Modeling the Continuous Time Random Walk}

  A continuous time random walk (CTRW) is a stochastic process characterized by a 
  distribution of hop lengths and dwell times.
  \begin{itemize}
	\item We use the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item We have limited data, so we attempted to approximate these distributions
	with known continuous probability densities.
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution while the distribution of dwell
	times fits relatively well to an exponential distribution characteristic of a
	Poisson process. (See supporting information)
  \end{itemize}

  \begin{equation}
	Ae^{-x}
  \end{equation}

  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
  magnitude longer than our molecular simulations. 
  \begin{itemize}
	\item We constructed trajectories by generating sequences of dwell times 
        and hop lengths randomly sampled from our fit distributions.
	\item For time scales much greater than the characteristic time of our
	exponential dwell time distribution, solutes exhibit Brownian motion. 
	\item The MSD curve becomes linear
	\item We fit a line to the MSD curve and used the Einstein relationship
	to relate its slope to the macroscopic diffusion coefficient.
	\item We found convergence of the value of the diffusion coefficient 
	calculated in this way afer x steps (See Supporting Information)
  \end{itemize}

  \subsection{Experimental}
  % BJC: For Greg to write if things work out

  \section{Results and Discussion}

  \section{Conclusion}

  \section*{Supporting Information}

  Detailed explanations and expansions upon the results and procedures mentioned in
  the main text are described in the Supporting Information. This information is
  available free of charge via the Internet at http://pubs.acs.org.

  \section*{Acknowledgements}

  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  \clearpage
  \bibliography{llc}

  \newpage

  \section*{TOC Graphic}

\end{document}

### 2018-11-30 Ben_Manuscripts/transport/Outline.tex
Updates

@@
 
-  We equilibrated our initial configuration before adding solutes.
+  We equilibrated an initial solvated configuration before adding solutes.
   \begin{itemize}
@@
 
-  \subsubsection*{Modeling the Continuous Time Random Walk}
+  \subsubsection*{Modeling the Continuous Time Random Walk}\label{method:CTRW}
 
@@
 
+  \subsection{Simulated Estimates of Macroscopic Diffusion Coefficients}\label{section:D_macro}
+
+  Polar molecules generally exhibit a hop diffusion mechanism. 
+  \begin{itemize}
+	\item Each trajectory is characterized by an exponential distribution of
+	dwell times between hops of random lengths from a Gaussian distribution.
+  \end{itemize}
+
+  We fit a CTRW model (see Section~\ref{method:CTRW}) to these 
+  trajectories and predicted macroscopic diffusion coefficients which are
+  presented in Table TBD.
+
+  % BJC: figure with selected trajectories for each molecule.
+
+  % BJC: table with finalized diffusion coefficients
+
+  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}
+
+  \subsection{Transport Mechanisms}
+
+  In order to truly understand the molecular origins of the macroscopic diffusion
+  coefficients in Section~\ref{section:D_macro}, we studied the microscopic interactions
+  between solutes and the membrane that lead to the observed dwell and hop distributions.
+
+  \subsubsection*{Transport of Water}
+
+  All water molecules exhibit hop diffusion.
+
+  Even in the center of the pore, where the density of water molecules is 
+  highest, individual water molecules still exhibit hop diffusion as they
+  create a tight hydrogen bond network.
+
+  In this confined environment, the diffusion constant is x times lower than
+  expected bulk diffusion coefficient of tip3p water.
+
+  \subsubsection*{Transport of Alcohols}
+
+  The hydroxyl functional group of alcohol molecules is a hydrogen bond donor
+  and prefers to donate it's hydrogen to strongly polarized carboxylate head
+  groups.
+
+  As alcohol groups increase in hydrophobic character, they are more inclined
+  to stick to the outside edges of the pore. 
+  \begin{itemize}
+	\item The alkane tails prefer to stay at the edges of the pore. 
+	\item They tend to get trapped between monomers and closer to 
+	the tail region. 
+	\item The entrapment is further stabilized by hydrogen bonds with
+	ether oxygens connecting the monomer's alkane tails to the head groups.
+  \end{itemize}
+
+  The diffusion coefficient of simple alcohols increases as the length of 
+  the alkane chain increases.
+  \begin{itemize}
+	\item The dwell times increase as the oily tails become more
+	entrapped in monomer tails.
+  \end{itemize}
+
+  Ethylene glycol, a diol, has two hydrogen bond donor groups.
+  \begin{itemize}
+	\item Can hydrogen bond with same moeity.
+	\item Can hydrogen bond with different moeities in the same 
+	vicinity. 
+	\item Dwell times tend to be shorter. If one hydroxyl group is bound
+	with a hydrogen bond, the other unbound hydroxyl group may form a hydrogen bond
+	elsewhere and effectively pull the other bound hydroxyl group along with it. 
+  \end{itemize}
+
+  \subsubsection*{Transport of Acetone}
+
+  The carbonyl group of Acetone is a hydrogen bond acceptor and therefore only
+  form hydrogen bonds with water molecules in the pore.
+
+  The hydrophobic character of the two methyl groups on acetone causes the methyl
+  groups to gravitate towards the outside of the pore, while the carbonyl group
+  reaches towards the pore center in order to
+
+  \subsubsection*{Transport of Acetic Acid}
+
+  Acetic acid, since we modeled it solely in its protonated state, has hydrogen
+  bond donor and acceptor groups.
+
+  \subsubsection*{Transport of Ions} % probably just sodium
+
+  \subsection{Experimental comparison of diffusion results}
+
+  % For Greg
+
   \section{Conclusion}
+
+  We have examined the transport characteristics of a series of small polar
+  molecules in our model of the H\textsubscript{II} phase formed by 
+  Na-GA3C11.
+
+  We calculated the macroscopic diffusion coefficients of each solute as 
+  approximated by a CTRW model.
+
+  We have studied the influence of water content on the diffusion coefficients.
+
+  We have validated our results using experimental DOSY NMR measurements.
+
+  We can use this intuition in order to modify our monomers for a specific 
+  separation.
+  \begin{itemize}
+	\item Increase number of h-bond sites to increase selectivity towards water 
+	over polar molecules
+	\item Also separate acetone (things with only h-bond accepting groups) in this way
+  \end{itemize}
 

### 2018-12-03 Ben_Manuscripts/transport/Outline.tex
Minor updates

@@
 
+  \subsubsection*{Radial Distribution Functions}
+
+  We measured the average radial distance of each solute of interest from the pore
+  centers.
+  \begin{itemize}
+	\item We binned the radial distances and then normalized by the volume
+	of the annulus defined by the bin edges.
+	\item Although the pores are often described as straight, they have a
+	small degree of tortuosity which disrupts the RDF calcuation 
+	\item We obtain the best RDF by constructing splines that run through the
+	pore centers.
+	\item We construct the splines by dividing the membrane into 20 slices
+	in the $z$-direction. Within each slice, we calculate the location of 
+	the pore centers based on the average location of the aromatic rings
+	that make up the monomer head groups.
+	\item When calculating the RDF, the radial distance from the pore center
+	is based on the distance between the solute center-of-mass and the ($x$, $y$)
+	coordinates of appropriate point on the spline.
+  \end{itemize}
+
   \subsection{Experimental}
@@
 
-  \subsection{Simulated Estimates of Macroscopic Diffusion Coefficients}\label{section:D_macro}
+  \subsection{Macroscopoic Diffusion Coefficients}
+
+  \subsection{Simulated Predictions}\label{section:D_macro}
 
@@
 
+  \subsection{Experimental Measurements}
+
+  % For Greg
+
   \subsection{Transport Mechanisms}
 
-  In order to truly understand the molecular origins of the macroscopic diffusion
-  coefficients in Section~\ref{section:D_macro}, we studied the microscopic interactions
-  between solutes and the membrane that lead to the observed dwell and hop distributions.
+  In order to truly understand the molecular origins of the macroscopic
+  diffusion coefficients in Section~\ref{section:D_macro}, we studied the
+  microscopic interactions between solutes and the membrane that lead to the
+  observed dwell time and hop distributions.
+  \begin{itemize}
+	\item We studied the radial distribution functions of solutes as a
+	function of distance from the pore center
+	\item We looked at hydrogen bonding patterns
+	\item Order parameters
+  \end{itemize}
+
+  The radial distribution function of each solute studied is shown in 
+  Figure TBD.
 
@@
   Even in the center of the pore, where the density of water molecules is
-  highest, individual water molecules still exhibit hop diffusion as they
-  create a tight hydrogen bond network.
+  highest, individual water molecules exhibit hop diffusion as they create a
+  tight hydrogen bond network.
+  %TODO: the following is a hypothesis
+  \begin{itemize}
+	\item Water sticks to pore walls
+	\item Dwell times are short
+	\item Water tumbles across pore for a while until it sticks again. 
+	\item Water gets caught in h-bonds with other water molecules away
+	from pore center.
+  \end{itemize}
 
@@
 
+  %TODO: study diffusion mechanism of water
+
   \subsubsection*{Transport of Alcohols}
@@
   The hydroxyl functional group of alcohol molecules is a hydrogen bond donor
-  and prefers to donate it's hydrogen to strongly polarized carboxylate head
+  and prefers to donate it's hydrogen to more strongly polarized carboxylate head
   groups.
@@
 	\item The alkane tails prefer to stay at the edges of the pore.
+	\item Radial distribution functions show peaks at pore edges, however
+	smaller alcohols have high densities near the pore center. 
 	\item They tend to get trapped between monomers and closer to 
@@
 	ether oxygens connecting the monomer's alkane tails to the head groups.
+	%TODO: quantify h-bonds with ether oxygens and carbonyl oxygens
   \end{itemize}
@@
   groups to gravitate towards the outside of the pore, while the carbonyl group
-  reaches towards the pore center in order to
+  reaches towards the pore center in order to hydrogen bond with water molecules.
+  \begin{itemize}
+	\item Order parameter defined between vector along carbonyl and vector extending
+	from acetone COM to pore center is non-zero.
+  \end{itemize}
 
@@
 
-  \subsection{Experimental comparison of diffusion results}
-
-  % For Greg
-
   \section{Conclusion}
@@
   We calculated the macroscopic diffusion coefficients of each solute as 
-  approximated by a CTRW model.
+  approximated by a CTRW model and validated our estimates using experimental
+  DOSY NMR measurements.
 
@@
 
-  We have validated our results using experimental DOSY NMR measurements.
+  We showed that hydrogen bonding between solutes and Na-GA3C11 monomers plays
+  a major role in mechanism by which molecules traverse the nanopores.
 

### 2018-12-05 analysis/msd.py
Justifying CTRW

@@ -10,30 +10,64 @@ from LLC_Membranes.analysis import Poly_fit, top, Atom_props, p2p
 import mdtraj as md
 import time
 from scipy import stats
+from scipy.optimize import curve_fit
 
 
 def initialize():
 
-    parser = argparse.ArgumentParser(description='Calculate diffusion coefficient')
+    parser = argparse.ArgumentParser(description='Calculate mean squared displacement (MSD) and diffusion coefficient'
+                                                 'for a specific residue or set of atoms in a trajectory')
     parser.add_argument('-t', '--trajectory', default='wiggle.trr', help='Path to input file')
     parser.add_argument('-g', '--gro', default='wiggle.gro', help='Name of .gro coordinate file')
     parser.add_argument('-r', '--residue', type=str, help='Name of residue whose diffusivity we want')
     parser.add_argument('-atoms', nargs='+', help='Name of atoms whose collective diffusivity is desired')
     parser.add_argument('-b', '--nboot', default=200, help='Number of bootstrap trials to be run')
-    parser.add_argument('-f', '--frontfrac', default=0.05, type=float, help='Where to start fitting line on msd curve')
+    parser.add_argument('-f', '--frontfrac', default=0, type=float, help='Where to start fitting line on msd curve')
     parser.add_argument('-F', '--fracshow', default=.2, type=float, help='Percent of graph to show, also where to stop '
                         'fitting line during diffusivity calculation')
     parser.add_argument('-a', '--axis', default='xyz', type=str, help='Which axis to compute msd along')
     parser.add_argument('-nboot', default=200, type=int, help='Number of bootstrap trials for error estimation')
+    parser.add_argument('-ensemble', action="store_true", help='Calculate MSD as ensemble average')
+    parser.add_argument('-compare', action="store_true", help='Compare time-averaged and ensemble-averaged time'
+                                                              'series')
+    parser.add_argument('-power_law', action="store_true", help='Fit MSD to a power law')
+
     # | not implemented |
     # v                 v
     parser.add_argument('--restrict_to_pores', action="store_true", help='Only look at residue within pores of HII'
[…]

### 2018-12-05 timeseries/forecast_ctrw.py

@@ -192,13 +192,14 @@ class System(object):
 
         if ma:
             self.calculate_moving_average(ma)
-
+        print(self.com.shape)
         # np.random.seed(2)
-        # # plot 5 random z-traces
-        # for i in np.random.randint(0, self.nres, size=5):
-        #     plt.plot(self.com[:, i, 2])
-        # plt.show()
-        # exit()
+        # plot 5 random z-traces
+        for i in np.random.randint(0, self.nres, size=5):
+            # print(54930 + i + 1)
+            plt.plot(self.com[:, i, 2])
+        plt.show()
+        exit()
 
         # initialize for later
         # self.xs = np.zeros()

### 2018-12-05 Ben_Manuscripts/transport/Outline.tex
Justifying CTRW
Updates

@@
 \title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
-\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}
+\author{Benjamin J. Coscia \and Michael R. Shirts}
 
 \begin{document}
-%  \bibliographystyle{ieeetr}
+
   \graphicspath{{./figures/}}
   \maketitle
+
   \section{Introduction}
@@
 	with known continuous probability densities.
+	\item Incorporates effects of `aging' since it samples long dwell times
 	\item For solutes in our system the distribution of hop lengths is
@@
 
+  Sodium ions also exhibit hop diffusion because polarized water and
+  carboxylate head groups both work to neutralize its charge.
+  \begin{itemize}
+	\item Ions get trapped in oxygen 'cages' composed of combinations
+	of water molecules, carboxylate head groups and ether oxygens connecting
+	the head groups to their tails.
+  	\item Interesting coordination number data
+	\item Dwell time proportional to surrounding charge within coordination shell
+  \end{itemize}
+
+  \subsubsection*{Remarks}
+
+  Overwhelming amount of water in 10 wt\% system makes hydrogen bonding
+  competitive between head groups and water.
+
+  \subsection{Design Suggestions}
+
+  Water content affects pore size. Experiments to understand this could be useful.
+
+  Separate polar molecules by creating monomers with more hydrophilic head group components.
+  More incentive to dwell on walls.
+
+  Make ions move faster by placing charges in sterically inaccessible places.
+
   \section{Conclusion}

### 2018-12-06 llclib/transform.py
Calculating coordination number

@@ -1,13 +1,14 @@
 #! /usr/bin/env python
 
 """
-Coordinate transforms and related manipulations of positions
+Commonly used coordinate transforms and related manipulations of positions, including fourier transforms
 """
 from __future__ import division
 from __future__ import print_function
 
 import numpy as np
 import math
+import tqdm
 
 
 def layer_dist(layers, nopores, distribution, monomers, alt_1, alt_2):
@@ -481,3 +482,73 @@ def random_orientation(xyz, alignment_vector, placement):
     rotated += placement  # translate to desired location
 
     return rotated
+
+
+def rescale(coords, dims):
+    """
+    rescale coordinates so that cell dimensions are constant over the simulation
+    returns rescaled coordinates and average length
+    """
+
+    avgdims = np.average(dims, axis=0)
+    a = avgdims / dims
+    rc = coords
+
+    for it in range(rc.shape[0]):
+        for i in range(3):
+            rc[it, :, i] *= a[it, i]
+
+    return rc, avgdims
+
+
+def monoclinic_to_cubic(xyz, theta=60):
+    """Convert monoclinic cell to cubic cell"""
+
+    print("transforming coordinates to monoclinic cell (theta={:3.2f} deg)".format(theta*180.0/np.pi))
+
+    coordinates = np.copy(xyz)
+    coordinates[..., 1] /= np.sin(theta)
+    coordinates[..., 0] -= coordinates[..., 1]*np.cos(theta)
+
+    return coordinates
+
+
+def fft_3D_monoclinic(xyz, box_vectors, bins, angle=60, sf=False):
+    """ Calculate 3D discrete fourier transform for each frame of a trajectory of coordinates in monoclinic unit cell
+
+    :param xyz: frame-by-frames coordinates of atoms whose 3D DFT we want to calculate
+    :param box_vectors: matrix of box vectors of shape (nT, 3, 3)
+    :param bins: number of bins in each dimension
+    :return:
+    """
+
+    nT = xyz.shape[0]  # number of frames
+    L = np.linalg.norm(box_vectors, axis=2)
+
+    locations, L = rescale(xyz, L)  # make unit cell constant size
+
+    # define histograme bin edges
+    x = np.linspace(0, L[0], int(bins[0]))
+    y = np.linspace(0, L[1], int(bins[1]))
+    z = np.linspace(0, L[2], int(bins[2]))
+
+    zv = [0.0, 0.0, 0.0]  # zero vector
+
[…]

### 2018-12-06 Ben_Manuscripts/transport/Outline.tex
Calculating coordination number
Updates

@@
 
-  In this work, we have determined the transport mechanisms and macroscopic transport 
-  properties exhibited by a number of polar solutes with varying size, chemical 
-  functionality and hydrophilic character.
+  In this work, we have determined the transport mechanisms and macroscopic
+  transport properties exhibited by a number of polar solutes with varying size,
+  chemical functionality and hydrophilic character.
   \begin{itemize}
@@
 
-  We have compared our calculated diffusion coefficients with experimental measurements
-  made using DOSY NMR.
+  We have compared our calculated diffusion coefficients with experimental
+  measurements made using DOSY NMR.
 
@@
 	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
+	\item See supporting info for water equilibration simulation data.
 	\item We adjusted the pore radius in our systems so that the right amount of water
@@
 
-  A continuous time random walk (CTRW) is a stochastic process characterized by a 
-  distribution of hop lengths and dwell times.
+  A continuous time random walk (CTRW) is a stochastic anomalous diffusion
+  process characterized by a distribution of hop lengths and dwell times.
+  \begin{itemize}
+	\item The MSD for an anomalous diffusion process is of the form $$t^\alpha$$
+	\item A value of $\alpha < 1$ tells us that the molecules exhibits subdiffusion
+	\item Subdiffusive, non-ergodic processes with uncorrelated steps help distinguish 
+	a CTRW from other anomalous subdiffusive process such as fraction brownian motion 
+	and random walks on a fractal.
+	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
+  \end{itemize}
+
+  We fit our data to a CTRW model by using our data in order to construct 
+  dwell time and hop length distributions.
   \begin{itemize}
@@
 	\item For solutes in our system the distribution of hop lengths is
-	well-represented by a Gaussian distribution while the distribution of dwell
-	times fits relatively well to an exponential distribution characteristic of a
-	Poisson process. (See supporting information)
+	well-represented by a Gaussian distribution 
+	\item The distribution of dwell	times is expected to fit a heavy tailed distribution: 
   \end{itemize}
@@
   \begin{equation}
-	Ae^{-x}
+	Ax^{(-1 - \alpha)}
   \end{equation}
@@
 	\item For time scales much greater than the characteristic time of our
-	exponential dwell time distribution, solutes exhibit Brownian motion. 
+	dwell time distribution, solutes exhibit Brownian motion. 
 	\item The MSD curve becomes linear
@@
 
+  \subsubsection*{Coordination number}
+
+  We quantified the coordination of solutes with surrounding molecules and
+  functional groups in two ways.
+  \begin{itemize}
+	\item By counting the number of coordinated molecules to a given solute
+	based on a distance cut-off. Gives frame-by-frame information. 
+	\item By averaging 3D spherical radial distribution function calculated for
+	each solute.
+  \end{itemize}
+
   \subsection{Experimental}
@@
 
-  \subsection{Macroscopoic Diffusion Coefficients}
+  \subsection{Macroscopic Diffusion Coefficients}
 
-  \subsection{Simulated Predictions}\label{section:D_macro}
+  \subsubsection{Simulated Predictions}\label{section:D_macro}
 
@@
   \begin{itemize}
-	\item Each trajectory is characterized by an exponential distribution of
+	\item Each trajectory is characterized by a power law distribution of
 	dwell times between hops of random lengths from a Gaussian distribution.
   \end{itemize}
+
+  % BJC: figure with selected trajectories for each molecule.
 
@@
   presented in Table TBD.
-
-  % BJC: figure with selected trajectories for each molecule.
+  \begin{itemize}
+	\item We confirmed that our molecules exhibit anomalous diffusion
+	by fitting a power law to the MSD curve. The exponent is less than
+	1, indicative of anomalous subdiffusion.
+	\item We used the decision making process given by Meroz and Sokolov
+	in order to identify the appropriate subdiffusion model to use 
+	based on our time series (See Section S-TBD of the Supporting info for
+	more details).
+	\item The motion of the solutes is non-ergodic and the steps are
+	uncorrelated which tells us the system is likely well-described
+	by a CTRW. 
+  \end{itemize}
 
@@
 
-  \subsection{Experimental Measurements}
+  Solutes in systems with lower water content exhibit lower diffusion coefficients.
+  \begin{itemize}
+	\item Pores are more crowded when there is less water (show RDFs of each)
+	\item Not a linear function of pore size - radius increase by x, D increases by y
+	\item Larger influence on bigger molecules
+  \end{itemize}
+
+  \subsubsection{Experimental Measurements}
 
@@
 	\item We looked at hydrogen bonding patterns
+	\item Coordination numbers
 	\item Order parameters

### 2018-12-07 Ben_Manuscripts/transport/Supporting_Information.tex
Added beginnings of Supporting information

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thetable}{S\arabic{table}}

\title{Supporting Information: The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

\begin{document}

  \maketitle
  \graphicspath{{./supporting_figures/}}
  \bibliographystyle{ieeetr}

  \section{Water content equilibration}\label{section:water_content_equil}

  We initially tried to equilibrate our system with water by allowing water
  molecules to naturally penetrate the membrane from a water bath separating
  periodic images of the system in the $z$-direction (See Figure~\ref{fig:gap}).
  We allowed a dry, previously equilibrated system to further equilibrate in
  coexistence with a 3 nm-thick (in the $z$-direction) layer of water. Water
  readily enters the tail region where the density of monomers is low. About 3
  times more water molecules occupy the tail region after 1000 ns of
  equilibration (See Figure~\ref{fig:equilibrated_water_penetration}). Although
  the water level in the pore appears to plateau in this system, it is clear that
  equilibration of this system is kinetically limited since water does not fill
  the pores uniformly. The density of water along the pore axis, averaged over
  the last 50 nanoseconds of simulation, is close to zero at the membrane center.
  Therefore, we required a different equilibration technique in order to overcome
  the kinetic limitation.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.18\textwidth}
  \includegraphics[width=\linewidth]{gap.pdf}
  \caption{}\label{fig:gap}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with : solute_partitioning.py -t shifted.xtc -g berendsen.gro -buffer 2 -r SOL
% in directory : /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/gaps/pre_equilibrated
  \includegraphics[width=\linewidth]{equilibrated_water_penetration.pdf}
  \caption{}\label{fig:equilibrated_water_penetration}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with custom script density.py located in same directory as above.
  \includegraphics[width=\linewidth]{penetration_density.pdf}
  \caption{}\label{fig:penetration_density}
  \end{subfigure}  
  \caption{(a) Using an equilibrated dry configuration, we inserted a layer of water between
           periodic copies of the system in the $z$-direction. (b) Water slowly enters 
	   the membrane. Most water enters the tail region where the density of monomers is
	   lowest. Water entering the pore plateaus after 500 ns. (c) Although the water
	   content of the pore appears equilibrated in (b), the density of water throughout
	   the pores is not uniform, with almost no water close to the pore center.
  }\label{fig:gap_solvation}
  \end{figure}

  We equilibrated 4 systems where we initially placed water in the pores and in
  the tails along with a water reservoir in between periodic images, much like
  Figure~\ref{fig:gap}. We tested a diverse set of systems with varying total
  water contents and ratios of pore : tail water contents. The intial pore radius
  dictates the water content of the pore if one is to avoid vacuum gaps. We
  explored systems with initial pore radii of 5, 6, 7 and 8 \AA. Table \_\_ shows
  the water composition of the pores and the tails for each system studied. In
  systems started with more water in the tails, the pore water tends to increase
  over time, while that of the tails decreases or stays stable. Systems started
  with more water in the pores tend to plateau relatively quickly, with $\sim$
  one third of the water staying in the tails.

  \begin{table}
  \centering
  \begin{tabular}{|c|c|c|}
  \hline
  Pore Radius & wt \% water tails & wt \% water pores \\
  \hline
  5           &        5.67       &     1.09          \\
  6           &        2.88       &     2.38          \\
  7           &        1.91       &     4.12          \\
  8           &        2.78       &     6.00          \\
  \hline
  \end{tabular}
  \caption{}\label{table:water_content}
  \end{table}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated by running: solute_partitioning.py -t stabilized.xtc -g PR.gro -buffer 3 --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/5/1.09_5.67
  \includegraphics[width=\linewidth]{r5_gap.pdf}
  \caption{r = 5\AA}\label{fig:r5_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g PR.gro -buffer 2.5 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/6/2.38_2.88
  \includegraphics[width=\linewidth]{r6_gap.pdf}
  \caption{r = 6\AA}\label{fig:r6_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g last.gro -buffer 3 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/6/4.12_1.91
  \includegraphics[width=\linewidth]{r7_gap.pdf}
  \caption{r = 7\AA}\label{fig:r7_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g last.gro -buffer 3 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/8/6.00_2.78
  \includegraphics[width=\linewidth]{r8_gap.pdf}
  \caption{r = 8\AA}\label{fig:r8_gap}
  \end{subfigure}
  \caption{}\label{fig:gap_prefilled_equil}
  \end{figure}

  Since the equilibrium water content is unclear based on the previous
  simulations, we elected to choose and study systems with two different water
  contents. We removed the water reservoir and allowed the pore and tail water
  contents to equilibrate with 5 and 10 wt \% water total. We placed one third of
  the total water needed in the tails. We considered the water content
  equilibrated once the water contents plateaued. The 10 wt \% water system
  equilibrated within the first 100 ns of simulation, while the 5 wt\% system did
  not plateau until $\sim$ 600 ns (See Figure~\ref{fig:solvation_equilibration}).
  The pores contain 72 \% and 69 \% of the total water in the 5 and 10 wt \%
  systems respectively.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t full_shifted.xtc -g berendsen.gro -r SOL -pr 1.6 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/5wt
  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
  \caption{}\label{fig:5wt_offset_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
  \caption{}\label{fig:10wt_offset_equil}
% Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/10wt
  \end{subfigure}
  \caption{We created solvated systems with one third of the total water
	  initially placed in the tail region. (a) With 5 wt \% total water, the water
	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
	  ns, with $\sim$ 69 \% the total water in the
	  pores.}\label{fig:solvation_equilibration}
  \end{figure}

  We cross-linked the equilibrated solvated systems, then allowed them to 
  equilibrate further for 100 ns.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  % To be made (10 wt % system in place for now)
  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
  \caption{}\label{fig:5wt_offset_xlinked_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
  \caption{}\label{fig:10wt_offset_xlinked_equil}
% Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/63_percent
  \end{subfigure}
  \caption{}\label{fig:solvation_equilibration}
  \end{figure}

  \section{Choosing a transport model}\label{section:transport_model_selection}

  We used the toolbox created by Meroz and Sokolov in order to justify our
  choice of transport model.\cite{meroz_toolbox_2015} The solutes in our systems
  exhibit anomalous transport properties characteristic of a Continuous Time
  Random Walk (CTRW).

  \subsection*{Mean Squared Displacement}

  The general form of a mean squared displacement (MSD) curve is:
  \begin{equation}
	\langle x^2(t) \rangle \sim t ^ \alpha
	\label{eqn:msd}
  \end{equation}
  For brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq
  1$, the particle of interest exhibits anomalous diffusion. Values of $\alpha$
  greater than 1 give rise to superdiffusion, while values of $\alpha$ less than
  1 give rise to subdiffusion.

  We can calculate the ensemble-averaged MSD curve by averaging the MSDs of
  each particle trajectory, where each MSD is calculated using:
  \begin{equation}
	\delta^2(t) = \| \mathbf{r}(t) - \mathbf{r}(0) \|^2
	\label{eqn:ensemble_msd}
  \end{equation}
  where $\|\cdot\|$ represents the Euclidean norm.

  The mean squared displacement of solutes in our model is a non-linear
  function of time, with $\alpha < 1$ which is indicative of anomalous
  subdiffusion. Figure \ref{fig:msd_power_law}a plots the ensemble-averaged MSD
  curve for 24 ethanol molecules diffusing in a 10 wt\% water H\textsubscript{II}
  LLC membrane system. We fit a power law of the form $Ae^{\alpha}$ to the MSD
  curve. We performed 2000 bootstrap trials by randomly sampling 24 MSD curves
  with replacement from the 24 total ethanol MSD curves. The bootstrapped average
  value of $\alpha$ is 0.75 for this system.

  \begin{figure}[!htb]
  \centering
% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -ensemble -power_law -a z -nboot 2000
% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
  \includegraphics[width=0.8\linewidth]{msd_power_law.pdf}
  \caption{(a) We fit a curve with the form of Equation~\ref{eqn:msd} to the
	  ensemble-averaged MSD curve. (b) The average value of $\alpha$, obtained using
	  fits to MSDs calculated from bootstrapped ensembles, is less than 1 suggesting
	  that ethanol molecules in our model exhibit subdiffusive
	  behavior.}\label{fig:msd_power_law}
  \end{figure}

  \subsection*{Ergodicity}

  The ergodicity of a system can help us narrow down the possible anomalous
  diffusion mechanisms. In an ergodic system, the time-averaged behavior of an
  observable should yield the same result as the ensemble average of the same
  observable. Examples of anomalous diffusion processes that are ergodic include
  random walks on fractals (RWF) and fractional brownian motion (FBM).
  Non-ergodic systems generally give rise to CTRWs with the possibility of
  combination with a RWF and/or FBM.\cite{meroz_toolbox_2015}

  We tested the ergodicity of our system by comparing the ensemble-averaged
  and time-averaged MSD curves. We calculated the MSD of each ethanol trajectory
  using Equation~\ref{eqn:ensemble_msd} and a time-averaged algorithm: 
  \begin{equation}
	\delta^2(t) = \dfrac{1}{N-t} \sum_{i=0}^{N-t-1} \| \mathbf{r}(i + t) - \mathbf{r}(i) \|^2
  \end{equation}
  where N is the total number of simulation frames, and t represents the length
  of subinterval or number of frames per subinterval. We averaged the MSD curves
  from each trajectory in order to create final MSD plots.

  The ethanol molecules exhibit non-ergodic behavior because their
  time-averaged and ensemble-averaged MSDs do not agree with each other
  (Figure~\ref{fig:ethanol_msd_comparison}). We validated our analysis using a 1
  ns simulation of a box of tip3p water molecules. As expected, since the
  particles exhibit Brownian motion, the time-averaged and ensemble-averaged MSDs
  agree with each within error (Figure~\ref{fig:water_box_msd_comparison}).

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -compare -nboot 2000 -a z
% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
  \includegraphics[width=\textwidth]{ethanol_msd_comparison.pdf}
  \caption{}\label{fig:ethanol_msd_comparison}
  \end{subfigure} 
  \begin{subfigure}{0.45\textwidth}
% Generated with msd.py -t traj_nojump.xtc -g npt.gro -r SOL -compare --fracshow 0.4 -nboot 2000 -a z
% in directory: /home/bcoscia/Documents/Gromacs/Transport/Solvent/solvent_boxes/pure_water
  \includegraphics[width=\textwidth]{water_box_msd_comparison.pdf}
  \caption{}\label{fig:water_box_msd_comparison}
  \end{subfigure} 
  \caption{(a) The time-averaged and the ensemble-averaged MSDs for ethanol in
	  an H\textsubscript{II} nanopore are not in agreement, implying non-ergodicity.
	  (b) A box of tip3p water molecules is expected to be ergodic and it is shown to
	  be true here because both MSDs are in agreement. }\label{fig:msd_comparison}
  \end{figure}

  \subsection*{Autocorrelation of steps}

% From Sokolov paper: "Assigning different waiting times τ i to each step, and assuming that the
% steps are uncorrelated as in a regular RW, gives rise to the CTRW model" -- I
% might need to check autocorrelation of steps lengths when a hop occurs rather
% than every time step. Not sure if there is enough data for that, but could check 
% a particularly hoppy trajectory after longer simulation.

  Based on the previous two sections, our model can likey be studied as a CTRW. 
  However, it is still possible that our CTRW model might also be convoluted with
  an FBM or a RWF process. In a pure CTRW, the steps are uncorrelated. 
  Both FBM and RWF exhibit anti-correlated steps.

  The steps in our system are not correlated. We showed this by calculating the
  autocorrelation function (ACF) of the step lengths in the $z$-direction. The
  ACF of a representative trajectory is shown in Figure~\ref{fig:eth_autocorrelation}.

  \begin{figure}[!htb]
  \centering
% Generated with brownian_test.py -t PR_nojump.xtc -g PR.gro -r ETH (and appropriate uncommenting -- need to rework that script)
% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
  \includegraphics[width=0.8\textwidth]{eth_autocorrelation.pdf}
  \caption{The autocorrelation function (right) of a representative ethanol
	   center of mass $z$-coordinate trajectory (left) almost immediately decays to zero,
	   indicating a complete loss of memory of it's previous position. Noise increases
	   at large time lags due to decreased sampling.}\label{fig:eth_autocorrelation}
  \end{figure}

  \clearpage
  \bibliography{transport}

\end{document}

### 2018-12-11 Ben_Manuscripts/transport/Supporting_Information.tex
New anomalous diffusion simulations

@@
 
-  We initially tried to equilibrate our system with water by allowing water
+  We initially attempted to equilibrate our system with water by allowing water
   molecules to naturally penetrate the membrane from a water bath separating
@@
 	   content of the pore appears equilibrated in (b), the density of water throughout
-	   the pores is not uniform, with almost no water close to the pore center.
+	   the pores is not uniform, with almost no water close to the pore center. Note that
+           the density is not shown below 3 nm or above 9.5 nm, because the the system
+	   enters the water layer at those points.
   }\label{fig:gap_solvation}
@@
   We equilibrated 4 systems where we initially placed water in the pores and in
-  the tails along with a water reservoir in between periodic images, much like
-  Figure~\ref{fig:gap}. We tested a diverse set of systems with varying total
-  water contents and ratios of pore : tail water contents. The intial pore radius
-  dictates the water content of the pore if one is to avoid vacuum gaps. We
-  explored systems with initial pore radii of 5, 6, 7 and 8 \AA. Table \_\_ shows
-  the water composition of the pores and the tails for each system studied. In
-  systems started with more water in the tails, the pore water tends to increase
-  over time, while that of the tails decreases or stays stable. Systems started
-  with more water in the pores tend to plateau relatively quickly, with $\sim$
-  one third of the water staying in the tails.
+  the tails in addition to a water reservoir between periodic images. We filled
+  the pores with water by running \texttt{gmx solvate} on our initial
+  configuration and removing any water molecules placed outside of the pore
+  region. The GROMACS command \texttt{gmx solvate} places water molecules in
+  proximity to other atoms based on their van der waals radii and therefore does
+  a decent job of preventing equilibration issues. This also means that the
+  intial pore radius dictates the water content of the pore. We can however, put
+  arbitrary amounts of water into the tail region. We chose to test systems with
+  initial pore radii of 5, 6, 7 and 8 \AA~with tail and pore water compositions
+  given in Table~\ref{table:water_content}.
 
-  \begin{table}
+  \begin{table}[!htb]
   \centering
@@
   \hline
-  Pore Radius & wt \% water tails & wt \% water pores \\
+  Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
   \hline
@@
   \end{tabular}
-  \caption{}\label{table:water_content}
+  \caption{We chose a diverse combination of initial pore and tail water
+	  contents in order to study its effect on equilibrium water
+	  content.}\label{table:water_content}
   \end{table}
 
-  \begin{figure}
+  Systems appear to be most stable when there is more water in the pores than
+  tails. In systems started with more water in the tails
+  (Figures~\ref{fig:r5_gap} and \ref{fig:r6_gap}), the pore water content tends
+  to increase over time, while that of the tails decreases or stays stable.
+  Filling the pores with water is likely a very long process since it requires
+  monomers to make space for water molecules. Systems started with a higher pore
+  water content (Figures~\ref{fig:r7_gap} and \ref{fig:r8_gap}) tend to plateau
+  relatively quickly, with about one third of the water staying in the tails.  We
+  used this ratio in order to construct the initial configurations used for the
+  studies in the main text.  Clearly, a more complicated methodology is needed in
+  order to predict the equilibrium water content of a given LLC membrane.
+  However, getting the value exactly right is not required for our study.
+  Instead, we can observe mechanisms as a function of water content in each
+  region.
+
+  \begin{figure}[!htb]
   \centering
@@
   contents. We removed the water reservoir and allowed the pore and tail water
-  contents to equilibrate with 5 and 10 wt \% water total. We placed one third of
-  the total water needed in the tails. We considered the water content
+  contents to equilibrate with 5 and 10 wt \% total water. We placed one third of
+  the total water needed in the tails, based on the intuition gained in
+  Figure~\ref{fig:gap_prefilled_equil}. We considered the water content
   equilibrated once the water contents plateaued. The 10 wt \% water system
@@
   \begin{subfigure}{0.45\textwidth}
-  % To be made (10 wt % system in place for now)
-  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
+% Generated with solute_partitioning.py -t PR.trr -g PR.gro -r SOL --savename SOL_partitioning.pl
+% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/5wt
+  \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
   \caption{}\label{fig:5wt_offset_xlinked_equil}
@@
 % Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
-% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/63_percent
+% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/10wt/63_percent
   \end{subfigure}

### 2018-12-11 llclib/timeseries.py

@@ -1,0 +1,237 @@
+#!/usr/bin/env python
+
+import numpy as np
+
+
+def largest_prime_factor(n):
+    i = 2
+    while i * i <= n:
+        if n % i:
+            i += 1
+        else:
+            n //= i
+    return n
+
+
+def acf_slow(d):
+    """ Calculate the autocorrelation function of a time series. This speed of this method is O(n^2)
+
+    :param d: numpy array of length n, with time series values {x1, x2 ... xn}
+    :return: autocorrelation function
+    """
+
+    # Subtract mean
+    d -= d.mean(axis=0)
+
+    autocorr = np.zeros([len(d)])
+    for l in range(d.shape[0]):  # cycle through lags
+        N = d.shape[0] - l
+        for n in range(N):
+            autocorr[l] += d[n] * d[n + l]
+        autocorr[l] /= N
+
+    autocorr /= d.var()
+
+    return autocorr
+
+
+def acf(t, largest_prime=500):
+
+    """ Quickly calculated the autocorrelation function of a time series, t. This gives the same results as acf_slow()
+    but uses FFTs. This method is faster than numpy.correlate. Efficiency is key in order to avoid headaches.
+
+    :param t: time series : ndarray [npoints, nseries]
+    :param largest_prime : the largest prime factor of array length allowed. The smaller the faster. 1.6M points takes
+    about 5 seconds with largest_prime=1000. Just be aware that you are losing data by truncating. But 5-6 data points
+    isn't a big deal for large arrays.
+
+    """
+
+    T = np.array(t)
+
+    # Don't allow a prime factor larger than 'largest_prime'. Truncate data until that condition is met
+    l = 2 * T.shape[0] - 1
+
+    while largest_prime_factor(l) >= largest_prime or l % 2 == 0:
+        l -= 1
+
+    T = T[:(l + 1) // 2, ...]  # '...' allows for no second dimension if only a single time series is analysed
+    length = T.shape[0] * 2 - 1
+
+    T -= np.mean(T, axis=0)
+
+    fftx = np.fft.fft(T, n=length, axis=0)
+    ret = np.fft.ifft(fftx * np.conjugate(fftx), axis=0)
+    ret = np.fft.fftshift(ret, axes=(0,))
+
+    autocorr_fxn = ret[length // 2:].real
+    autocorr_fxn /= np.arange(T.shape[0], 0, -1)[:, ...]
+    autocorr_fxn /= np.var(T, axis=0)
+
+    return autocorr_fxn  # normalized
+
+
[…]

### 2019-01-08 Ben_Manuscripts/transport/Outline.tex
Up to date methods for CTRW simulation

@@
 \usepackage{amsmath} % or simply amstext
+\usepackage{amssymb}
 \usepackage{siunitx}
@@
 
+  %MRS: may need to discuss the fact that the amount of water present in the tails may 
+  %MRS: or may not be experimentally consistent; but if we don't put it in, the results will 
+  %MRS: not be thermodynamically consistent, which will give issues with measurements and calculations.
+  %MRS2: hopefully, some experiments could let us know about different diffusion regimes . . . 
   We observed that water partitions into the tail region of our system and therefore
@@
 	\item 6 solutes per pore provided a balance of a useful amount of data
-	for generating statistics and a low degree of interaction between solutes
+	for generating statistics and a low degree of interaction between solutes (reference
+	to supporting information to show low degree of interaction)
 	\item At each insertion point we placed a randomly oriented solute molecule
@@
 	\item We collected transport data using long simulations, on the order of
-	1 microsecond, with pressure controlled by the Parrinello-Rahman barostat.
+	1 microsecond
+	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
   \end{itemize}
@@
   \begin{itemize}
-	\item The MSD for an anomalous diffusion process is of the form $$t^\alpha$$
-	\item A value of $\alpha < 1$ tells us that the molecules exhibits subdiffusion
-	\item Subdiffusive, non-ergodic processes with uncorrelated steps help distinguish 
-	a CTRW from other anomalous subdiffusive process such as fraction brownian motion 
-	and random walks on a fractal.
+	\item The MSD for an anomalous diffusion process is of the form
+	\begin{equation} 
+	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
+	\label{eqn:msd_form}
+	\end{equation} 
+	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
+	generalized diffusion coefficient. 
+	\item A value of $\alpha < 1$ indicates a subdiffusive process.
+	\item Subdiffusive, non-ergodic processes with uncorrelated steps distinguish 
+	a CTRW from other anomalous subdiffusive process such as fractional brownian motion 
+	and random walks on a fractal.~\cite{meroz_toolbox_2015}
 	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
@@
 
-  We fit our data to a CTRW model by using our data in order to construct 
-  dwell time and hop length distributions.
+  We obtained maximum likelihood estimates (MLE) of the parameters used to fit our
+  emperical dwell and hop length distributions to analytical functions.
   \begin{itemize}
-	\item We use the \texttt{ruptures} python package in order to identify
+	\item We used the \texttt{ruptures} python package in order to identify
 	breakpoints in solute trajectories. (See Supporting Information for more
@@
 	tolerance, number of dimensions used)
-	\item We have limited data, so we attempted to approximate these distributions
-	with known continuous probability densities.
-	\item Incorporates effects of `aging' since it samples long dwell times
+	\item The corresponding hop lengths and dwell times between break points were 
+	used to construct emperical distributions.
 	\item For solutes in our system the distribution of hop lengths is
-	well-represented by a Gaussian distribution 
-	\item The distribution of dwell	times is expected to fit a heavy tailed distribution: 
+	well-represented by a Gaussian distribution (Which has been often used in
+	literature)
+	\item The maximum likelihood estimate of Gaussian parameters is given simply
+	by the mean and standard deviation of the emperical data.
+	~\cite{metzler_random_2000,metzler_anomalous_2014,neusius_subdiffusion_2009} 
+	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
+	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
+	\item Because we are limited to taking measurements at discrete values
+	dictated by the output frequency of our simulation trajectories, we fit the
+	emperical dwell times to a discrete power law distribution whose maximum
+	likelihood $\alpha$ parameter we calculated by maximizing the following
+	likelihood function: 
+        \begin{equation}
+	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
+	\beta\sum_{i=1}^{n} \text{ln}~x_i 
+	\label{eqn:powelaw_likelihood}
+	\end{equation}
+	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
+	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
+	where $x_{min}$ is the smallest measured value of
+	$x_i$.~\cite{clauset_power-law_2009} 
+	%\item Incorporates effects of `aging' since it samples long dwell times
   \end{itemize}
 
+  %BJC: not sure following explanation is necessary. Could put thesis statement
+  % in previous paragraph.
+  We generated distributions of parameters for the dwell time and hop length
+  distributions using statistical bootstrapping.
+  \begin{itemize}
+	\item For each type of distribution, we randomly selected $n$ data points from the emperical
+	distribution with replacement.
+	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
+  \end{itemize}
+
+%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
+%  magnitude longer than our molecular simulations.
+  We simulated trajectories order of magnitude longer than our molecular simulations. 
+  \begin{itemize}
+	\item We constructed 10000, 10000 timestep trajectories by generating
+	sequences of dwell times and hop lengths randomly sampled from the appropriate
+	distributions.
+	\item For each trajectory, the parameters used to define each distribution were
+	randomly drawn from the bootstrapped parameter distributions.
+	\item We randomly sample Gaussian hop lengths using the
+	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
+	\item We randomly sampled dwell times from a discrete power law
+	distribution based on the reccomendations of Clauset et
+	al.~\cite{clauset_power-law_2009}: 
 	\begin{equation}
-	Ax^{(-1 - \alpha)}
+	x = \lfloor
+	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
+	\label{eqn:discrete_powerlaw_draws}
 	\end{equation}
+	where $r$ is randomly drawn from a uniform distribution which we simulated
+	with \texttt{numpy.random.uniform}.
+	\item We found that thermal noise does not significantly influence the MSD and
+	therefore did not add any noise to the simulated trajectories. (See supporting info)
+  \end{itemize}
 
-  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
-  magnitude longer than our molecular simulations. 
+  We calculated both the ensemble-averaged and time-averaged mean squared displacements (MSDs)
+  of the simulated trajectories.
   \begin{itemize}
-	\item We constructed trajectories by generating sequences of dwell times 
-        and hop lengths randomly sampled from our fit distributions.
-	\item For time scales much greater than the characteristic time of our
-	dwell time distribution, solutes exhibit Brownian motion. 
-	\item The MSD curve becomes linear
-	\item We fit a line to the MSD curve and used the Einstein relationship
-	to relate its slope to the macroscopic diffusion coefficient.
-	\item We found convergence of the value of the diffusion coefficient 
-	calculated in this way afer x steps (See Supporting Information)
+	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
+	position ~\cite{meroz_toolbox_2015} and can be written as
+	\begin{equation}
+	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
+	\label{eqn:ensemble_msd}
+	\end{equation}
+	\item The average MSD calculated in this way recovers the form of
+	Equation~\ref{eqn:msd_form}. 
+	\item The time-averaged MSD measures the displacement between all possible time lags
+	and can be written as
+	\begin{equation}
+	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}{T - \tau} (x(t + \tau) - x(t))^2 dt
+	\end{equation}
+	where $\tau$ is the time lage and T is the length of the
+	trajectory~\cite{meroz_toolbox_2015}. 
+	\item The time-averaged MSD becomes linear in our simulations,
+	therefore we can fit a line to its slope in order to estimate the macroscopic
+	diffusivity of the particle.
+	%BJC: this needs more justification. Not many people have done it
+	%BJC: could also not report them as diffusivities. Comparison of total MSD
+	% should give same information
+	% Linear region probably exists because dwell times on the order of large lag times
+	% become negligible
   \end{itemize}
+
+  We fixed the length of each simulated trajectory so that we could compare the total
+  MSD between different solutes without the influence of the ageing phenomenon.
+  \begin{item}
+	\item Ageing is defined by the tendency of the average MSD to decrease
+	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
+	\item The maximum measured dwell time can be no longer than the total length
+	of a simulated trajectory. 
+	\item As measurement time or trajectory length is increased, longer dwell times
+	are incorporated into the calculation, lowering the average MSD. (See supporting
+	info for demonstration)
+	\item We can achieve consistent total MSDs with low uncertainty for
+	simulated trajectories created with a given set of parameters if we fix the
+	trajectory length (as opposed to total number of steps).  
+  \end{item}
 
@@
 
-  We quantified the coordination of solutes with surrounding molecules and
-  functional groups in two ways.
+  We quantified the coordination of solutes with surrounding molecules.
   \begin{itemize}
-	\item By counting the number of coordinated molecules to a given solute
-	based on a distance cut-off. Gives frame-by-frame information. 
-	\item By averaging 3D spherical radial distribution function calculated for
-	each solute.
+  	\item For each frame, we counted the identites and number of
+  	coordinated molecules to a given solute based on a distance cut-off. 
+	\item We found that this approach is more useful than calculating the
+	3D spherical radial distribution function because it gives detailed
+	frame-by-frame information rather than an average. 
   \end{itemize}
@@
 
-  \subsection{Macroscopic Diffusion Coefficients}
-
-  \subsubsection{Simulated Predictions}\label{section:D_macro}
+  \subsection{Simulated Predictions}\label{section:D_macro}
 
@@
   competitive between head groups and water.
+  %MRS: not sure what you mean above.
 
@@
   \clearpage
-  \bibliography{llc}
+
+  \bibliographystyle{ieeetr}
+  \bibliography{Transport}
 

### 2019-01-10 timeseries/fbmsim.py
new demos and minor fixes

@@ -6,7 +6,7 @@ import matplotlib.pyplot as plt
 from LLC_Membranes.analysis import Poly_fit
 from LLC_Membranes.llclib import timeseries, fitting_functions
 import tqdm
-import fbm
+from fbm_fork import fbm
 
 
 def initialize():
@@ -22,15 +22,18 @@ def initialize():
     parser.add_argument('-fdt', '--ftimestep', default=1, type=float, help='Time step between steps in fractional '
                         'brownian motion simulated trajectory (arbitrary units).')
     parser.add_argument('-acf', '--autocorrelation', action="store_true", help='Plot step autocorrelation function')
+    parser.add_argument('-acov', '--autocovariance', action="store_true", help='Plot autocovariance of fractional'
+                                                                               'gaussian noise')
     parser.add_argument('-ensemble', '--ensemble', action="store_true", help='Calculate MSD as ensemble average')
     parser.add_argument('-power_law', '--power_law', action="store_true", help='Fit MSD to a power law')
+    parser.add_argument('-scale', '--scale', default=None, type=float, help='Sigma of hop length distribution')
 
     return parser
 
 
 class FractionalBrownianMotion(object):
 
-    def __init__(self, nsteps, hurst, ntraj=1, length=2, method="daviesharte"):
+    def __init__(self, nsteps, hurst, ntraj=1, length=1, method="daviesharte", scale=None):
         """ Generate trajectories exhibiting fractional brownian motion
 
         :param nsteps: number of steps in trajectory
@@ -44,8 +47,8 @@ class FractionalBrownianMotion(object):
         self.ntraj = ntraj
         self.nsteps = nsteps
 
-        self.fbm = fbm.FBM(self.nsteps, self.hurst, length=length, method=method)
-        self.time = self.fbm.times()
+        self.fbm = fbm.FBM(self.nsteps, self.hurst, length=length, method=method, scale=scale)
+        self.time = fbm.times(self.nsteps, length=length)
 
         self.trajectories = np.zeros([nsteps + 1, ntraj])
 
@@ -56,6 +59,7 @@ class FractionalBrownianMotion(object):
         self.msd = None
         self.fit_parameters = None
         self.acf = None
+        self.acov = None
 
     def plot_fbm(self):
         """ Plot a fractional brownian motion trajectory using parameters in __init__
[…]

### 2019-01-19 Ben_Manuscripts/transport/Outline.tex
new demos and minor fixes
Upates to methods and addition of results

--- 2018-12-06 Ben_Manuscripts/transport/Outline.tex
@@
 	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
+	\item The amount of water present in the tails may or may not be experimentally consistent
+	but if we don't put it in, the results will not be thermodynamically consistent, which 
+	will give issues with measurements and calculations.
 	\item See supporting info for water equilibration simulation data.
@@
 	\item We equilibrated the initial configuration using the `wet'
-	equilibration procedure described in our previous work (reference to structure
-	paper).
+	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
 	\item We cross-linked the equilibrated solvated configuration using the
@@
 	\item We collected transport data using long simulations, on the order of
-	1 microsecond, with pressure controlled by the Parrinello-Rahman barostat.
+	1 microsecond
+	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
   \end{itemize}
 
-  \subsubsection*{Modeling the Continuous Time Random Walk}\label{method:CTRW}
+  \subsubsection*{Modeling subdiffusion}\label{method:CTRW}
 
-  A continuous time random walk (CTRW) is a stochastic anomalous diffusion
-  process characterized by a distribution of hop lengths and dwell times.
+  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
+  behavior, a type of anomalous diffusion. 
   \begin{itemize}
-	\item The MSD for an anomalous diffusion process is of the form $$t^\alpha$$
-	\item A value of $\alpha < 1$ tells us that the molecules exhibits subdiffusion
-	\item Subdiffusive, non-ergodic processes with uncorrelated steps help distinguish 
-	a CTRW from other anomalous subdiffusive process such as fraction brownian motion 
-	and random walks on a fractal.
-	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
+  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
+  	does not grow linearly with time, rather it is of the form:
+	\begin{equation} 
+	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
+	\label{eqn:msd_form}
+	\end{equation} 
+	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
+	generalized diffusion coefficient.
+	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
+	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
+	motion respectively.
   \end{itemize}
 
-  We fit our data to a CTRW model by using our data in order to construct 
-  dwell time and hop length distributions.
+  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
+  of the simulated trajectories.
   \begin{itemize}
-	\item We use the \texttt{ruptures} python package in order to identify
-	breakpoints in solute trajectories. (See Supporting Information for more
+	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
+	position~\cite{meroz_toolbox_2015} and can be written as
+	\begin{equation}
+	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
+	\label{eqn:ensemble_msd}
+	\end{equation}
+%	\item The average MSD calculated in this way recovers the form of
+%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
+	\item The time-averaged MSD measures the displacement between all possible time lags
+	and can be written as
+	\begin{equation}
+	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
+	\end{equation}
+	where $\tau$ is the time lag and T is the length of the
+	trajectory~\cite{meroz_toolbox_2015}. 
+%	\item The time-averaged MSD becomes linear in our simulations,
+%	therefore we can fit a line to its slope in order to estimate the macroscopic
+%	diffusivity of the particle.
+	%BJC: this needs more justification. Not many people have done it
+	%BJC: could also not report them as diffusivities. Comparison of total MSD
+	% should give same information
+	% Linear region probably exists because dwell times on the order of large lag times
+	% become negligible
+  \end{itemize}
+
+  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
+  continuous time random walks (CTRW), fractional Brownian motion (FBM) and
+  random walks on fractals (RWF).\cite{meroz_toolbox_2015}
+  \begin{itemize}
+    \item FBM is common in crowded, viscoelastic environments where each step comes 
+    from a Gaussian distribution but is anti-correlated to its previous 
+    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
+    \item A CTRW is characterized by a distribution of hop lengths and 
+    dwell times, where each each step is characterized by independent random draws from 
+    each distribution.\cite{montroll_random_1965,morrin_three_2018}
+    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
+    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
+    \item The processes described above can happen alone or in combination.  	
+  \end{itemize}
+
+  \noindent We believe that solutes in the system studied here exhibit subordinated 
+  fractional Brownian motion (sFBM) where the parent process is FBM and the 
+  leading process is a CTRW. 
+  \begin{itemize}
+  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
+  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
+  	\item We also observe non-stationary $z$-coordinate traces of each solute's
+  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
+  	\item For a pure CTRW, the time-averaged MSD should be linear.
+  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
+  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
+  	information), which suggests that there is another underlying subdiffusive mechanism.
+  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
+  	\item Given the viscoelastic nature of the monomers in our system, we believe
+  	the hop lengths can be modeled with FBM. 
+ 	\item For subordinated FBM, it can be shown that
+  	\begin{equation}
+  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
+  	\end{equation}
+  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
+  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
+  \end{itemize}
+
+  \noindent We can characterize a CTRW process using the parameters which describe its
+  dwell time and hop length distribution.
+  \begin{itemize}
+	\item We used the \texttt{ruptures} python package in order to identify
+	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
 	details on chosen parameters. i.e. type of cost function, cost function penalty
 	tolerance, number of dimensions used)
-	\item We have limited data, so we attempted to approximate these distributions
-	with known continuous probability densities.
-	\item Incorporates effects of `aging' since it samples long dwell times
-	\item For solutes in our system the distribution of hop lengths is
-	well-represented by a Gaussian distribution 
-	\item The distribution of dwell	times is expected to fit a heavy tailed distribution: 
+	\item The corresponding hop lengths and dwell times between break points were 
+	used to construct empirical distributions.
+	\item For solutes in our system, the distribution of hop lengths is
+	well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
+	metzler_anomalous_2014,neusius_subdiffusion_2009}
+	\item We are most interested in the standard deviation, $\sigma$, of the 
+	hop length distribution.
+	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
+	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
+	\item Because we are limited to taking measurements at discrete values
+	dictated by the output frequency of our simulation trajectories, we fit the
+	empirical dwell times to a discrete power law distribution whose maximum
+	likelihood $\alpha$ parameter we calculated by maximizing the following
+	likelihood function: 
+        \begin{equation}
+	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
+	\beta\sum_{i=1}^{n} \text{ln}~x_i 
+	\label{eqn:powerlaw_likelihood}
+	\end{equation}
+	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
+	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
+	where $x_{min}$ is the smallest measured value of
+	$x_i$.~\cite{clauset_power-law_2009} 
+	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
+	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
   \end{itemize}
 
+  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
+  $H = \beta/2$.
+  \begin{itemize}
+  	\item Brownian motion is recovered for $H = 0.5$
+	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
     \begin{equation}
-	Ax^{(-1 - \alpha)}
+	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
+	\label{eqn:autocovariance}
 	\end{equation}
+	where $k$ is the number of increments between hops.
+	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
+	to the empirically measured autocovariance function.
+	\item We used statistical bootstrapping to generate a distribution of $H$ 
+	values. %BJC: can provide more detail in supporting or just reference python script
+  \end{itemize}
 
-  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
-  magnitude longer than our molecular simulations. 
+%  We generated distributions of parameters for the dwell time and hop length
+%  distributions using statistical bootstrapping.
+%  \begin{itemize}
+%	\item For each type of distribution, we randomly selected $n$ data points from the empirical
+%	distribution with replacement.
+%	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
+%  \end{itemize}
+
+%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
+%  magnitude longer than our molecular simulations.
+  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
   \begin{itemize}
-	\item We constructed trajectories by generating sequences of dwell times 
-        and hop lengths randomly sampled from our fit distributions.
-	\item For time scales much greater than the characteristic time of our
-	dwell time distribution, solutes exhibit Brownian motion. 
-	\item The MSD curve becomes linear
-	\item We fit a line to the MSD curve and used the Einstein relationship
-	to relate its slope to the macroscopic diffusion coefficient.
-	\item We found convergence of the value of the diffusion coefficient 
-	calculated in this way afer x steps (See Supporting Information)
+	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
+	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
+	distributions.
+	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
+	the last data point so that the total time exactly equaled 1 $\mu$s. 
+    \item Valid comparisons are only possible between fixed length sFBM simulations. The
+    power law dwell time behavior gives rise to the aging phenomenon, embodied by
+    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
+    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
+% Following probably better suited for supporting information, if included at all
+%	\item We randomly sample Gaussian hop lengths using the
+%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
+%	\item We randomly sampled dwell times from a discrete power law
+%	distribution based on the recommendations of Clauset et
+%	al.~\cite{clauset_power-law_2009}: 
+%	\begin{equation}
+%	x = \lfloor
+%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
+%	\label{eqn:discrete_powerlaw_draws}
+%	\end{equation}
+%	where $r$ is randomly drawn from a uniform distribution which we simulated
+%	with \texttt{numpy.random.uniform}.
+%	\item We found that thermal noise does not significantly influence the MSD and
+%	therefore did not add any noise to the simulated trajectories. (See supporting info)
   \end{itemize}
+
+%BJC: probably don't need to explain this in great detail
+%  \noindent We fixed the length of each simulated trajectory so that we could compare the total
+%  MSD between different solutes without the influence of the ageing phenomenon.
+%  \begin{itemize}
+%	\item Ageing is defined by the tendency of the average MSD to decrease
+%	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
+%	\item The maximum measured dwell time can be no longer than the total length
+%	of a simulated trajectory. 
+%	\item As measurement time or trajectory length is increased, longer dwell times
+%	are incorporated into the calculation, lowering the average MSD. (See supporting
+%	info for demonstration)
+%	\item We can achieve consistent total MSDs with low uncertainty for
+%	simulated trajectories created with a given set of parameters if we fix the
+%	trajectory length (as opposed to total number of steps).  
+%  \end{itemize}
 
@@
 
-  We quantified the coordination of solutes with surrounding molecules and
-  functional groups in two ways.
+  We quantified the coordination of solutes with surrounding molecules.
   \begin{itemize}
-	\item By counting the number of coordinated molecules to a given solute
-	based on a distance cut-off. Gives frame-by-frame information. 
-	\item By averaging 3D spherical radial distribution function calculated for
-	each solute.
+  	\item For each frame, we counted the identities and number of
+  	coordinated molecules to a given solute based on a distance cut-off. 
+	\item We found that this approach is more useful than calculating the
+	3D spherical radial distribution function because it gives detailed
+	frame-by-frame information rather than an average. 
   \end{itemize}
@@
 
-  \subsection{Macroscopic Diffusion Coefficients}
+  \subsection{Simulated Predictions}\label{section:D_macro}
 
-  \subsubsection{Simulated Predictions}\label{section:D_macro}
+  We extracted values of $\sigma$, $\alpha$ and $H$ for each solute and then
+  simulated 10000 solutes trajectories as described in the Methods. The results
+  are presented in Table~\ref{table:simulations}.
+
+  % Add MD calculated MSD to this?
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{ccccc}
+  \toprule
+  System & $\sigma$ ($nm$) & $\alpha$ & $H$ & Simulated MSD ($nm^2$)\\
+  \midrule
+  Methanol & 0.46 & 0.85 & 0.40 & 55.06 [49.26, 60.58] \\
+  Urea & 0.33 & 0.64 & 0.40 & 15.64 [14.08, 17.32] \\
+  Ethylene Glycol & 0.35 & 0.64 & 0.36 & 6.30 [5.69, 6.93] \\
+  Acetic Acid & 0.28 & 0.51 & 0.43 & 4.11 [3.66, 4.65] \\
+  Mercaptoethanol & 0.32 & 0.58 & 0.37 & 2.54 [2.16, 2.93] \\
+  Propylene Glycol & 0.26 & 0.50 & 0.43 & 1.94 [1.70, 2.17] \\
+  Ethanol & 0.32 & 0.55 & 0.26 & 1.29 [1.14, 1.43] \\
+  Propanol & 0.25 & 0.41 & 0.39 & 1.13 [1.01, 1.27] \\
+  Glycerol & 0.22 & 0.46 & 0.37 & 1.09 [0.98, 1.20] \\
+  Ethyl Acetate & 0.21 & 0.42 & 0.37 & 0.82 [0.74, 0.91] \\
+  Acetone & 0.23 & 0.44 & 0.34 & 0.80 [0.70, 0.88] \\
+  Dimethyl Sulfoxide & 0.25 & 0.47 & 0.29 & 0.74 [0.65, 0.82] \\
+  Tetrose & 0.22 & 0.43 & 0.20 & 0.68 [0.61, 0.75] \\
+  Acetamide & 0.27 & 0.52 & 0.21 & 0.56 [0.51, 0.64] \\
+  2,3-Dimercapto-1-propanol & 0.20 & 0.38 & 0.37 & 0.53 [0.47, 0.58] \\
+  Butanol & 0.19 & 0.41 & 0.33 & 0.42 [0.36, 0.49] \\
+  Propylene Carbonate & 0.19 & 0.38 & 0.29 & 0.30 [0.26, 0.34] \\
+  Tetrahydrofuran & 0.25 & 0.40 & 0.24 & 0.29 [0.25, 0.34] \\
+  Dimethyl Formamide & 0.20 & 0.39 & 0.27 & 0.27 [0.24, 0.31] \\
+  Ribose & 0.21 & 0.43 & 0.23 & 0.27 [0.24, 0.31] \\
+  \bottomrule
+  \end{tabular}
+  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
+  trajectories and then computed the average ensemble-averaged MSD of 10000 
+  simulated trajectories.}\label{table:simulations}
+  \end{table}
+
+  It most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the simulated
+  simulated MSD values presented in Table~\ref{table:simulations}. 
+  \begin{itemize}
+  	\item Higher values of $\sigma$ indicate larger average hop lengths.
+  	\item Higher values of $\alpha$ mean that there will be less sampling of 
+  	long dwell times.
+  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
+  	of anti-correlation.
+  	\item All of which contribute to an overall increase in the simulated MSD
+  \end{itemize}
 
@@
   \clearpage
-  \bibliography{llc}
+
+  \bibliographystyle{ieeetr}
+  \bibliography{transport}
 

### 2019-01-19 analysis/molecular_geometry.py

@@ -8,6 +8,8 @@ from scipy.spatial import distance, ConvexHull
 from scipy.linalg import lstsq
 from LLC_Membranes.llclib import topology
 import tqdm
+import sqlite3 as sql
+import os
 
 
 def initialize():
@@ -19,6 +21,7 @@ def initialize():
                                                                             'must remain whole throughout simulation')
     parser.add_argument('-g', '--gro', default='em.gro', help='Name of .gro coordinate file.')
     parser.add_argument('-r', '--residue', default='ETH', help='Name of residue whose radius we want to calculate')
+    parser.add_argument('--update', action="store_true", help="update database with geometric values")
 
     return parser
 
@@ -60,6 +63,9 @@ class Geometry(object):
         self.radius = None
         self.volume = None
         self.planarity = None
+        self.ellipse_parameters = None
+        self.ellipse_uncertainty = None
+        self.location = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file__)))  # This script location
 
     def calculate_radius(self):
         """ Calculate longest atom-atom distance at each frame of trajectory
@@ -158,28 +164,23 @@ class Geometry(object):
 
     def fit_ellipsoid(self):
 
+        self.ellipse_parameters = np.zeros([self.nframes, self.nres, 3])
+
         for t in tqdm.tqdm(range(self.nframes)):
             for r in range(self.nres):
                 coords = self.xyz[t, self.res_ndx[r, :], :]  # coordinates to which we want to fit plane
 
                 # Perform principal component analysis to figure out direction where greatest variance occurs
-                y = (coords - np.mean(coords, axis=0)) * (1 / np.std(coords, axis=0)) # scale so mean is 0 and variance is 1
-                cov = np.cov(y.T)  # covariance matrix
+                # y = (coords - np.mean(coords, axis=0)) * (1 / np.std(coords, axis=0)) # scale so mean is 0 and variance is 1
+                cov = np.cov(coords.T)  # covariance matrix
                 eig_vals, eig_vecs = np.linalg.eig(cov)  # eigenvectors are all perpendicular to each other
-                sorted_ = eig_vecs[:, np.argsort(np.abs(eig_vals))[::-1]] # sort eigenvectors based on magnitude of eigen_values
 
-                # Largest 2 eigenvectors define plane
-                # Create rotation matrix that will make plane coplanar with xy plane
[…]

### 2019-01-30 Ben_Manuscripts/transport/Outline.tex
Added test

@@
 
-\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+%BJC: potential titles (uncommented is current favorite)
+%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
 
-  \subsubsection*{Modeling subdiffusion}\label{method:CTRW}
+  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}
 
@@
 
-  \subsection{Simulated Predictions}\label{section:D_macro}
+  \subsection{Governing Mechanisms}\label{section:mechanism_overview}
 
-  We extracted values of $\sigma$, $\alpha$ and $H$ for each solute and then
-  simulated 10000 solutes trajectories as described in the Methods. The results
+  % BJC: seems right to summarize overarching mechanisms observed first
+  The mechanisms which govern transport of small polar solutes in this 
+  system can be broadly described based a solute's size, shape, and polarity.
+  \begin{itemize}
+    \item In general, solutes can move fastest in the pore center, where
+    there is comparatively little resistance to diffusion. 
+  	\item The well-established trend of decreasing solute mobility with 
+  	size is not defied here, however we observe small solutes with lower-than-expected
+  	MSDs because they spend time trapped between monomer head groups.
+  	\item Additionally, planar molecules are prone to exhibiting similar
+  	trapping behavior, even for large molecules whose similar sized, but flexible
+  	counterparts exhibit faster diffusion.  %BJC: this is unproven
+  	\item The polarity of solutes also influences a solute's ability to stay in
+  	the pore center. Highly polar molecules tend to spend more time in the pore center,
+  	while those with hydrophobic character tend to spend more time in the head group
+  	region.
+  	\item Finally, the ability to hydrogen bond offers a second trapping mechanism. 
+  	Solutes that are hydrogen bond donors can donate hydrogen atoms to
+  	any of the 5 oxygen atoms located on the monomer head groups. Increasing the 
+  	number of hydrogen bond donating groups increases the solute's polarity causing
+  	solutes to spend more time in the pore centers, but the effect can be countered
+  	by excessive trapping if there many hydrogen bonds are being formed.
+  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
+  	mechanisms, with anticorrelated hops between each period of immobility due to 
+  	obstructions.
+  \end{itemize}
+
+  \end{itemize}
+
+  We will explore these factors in greater detail in the context of 
+  specific groups of molecules in the discussion that follows.
+
+  \subsection{MSD Predictions}\label{section:msd_predictions}
+
+  %BJC: focus on MD MSD results
+  \noindent We calculated the MSD of each solute in the set over the course of 1$\mu$s MD simulations.  %BJC: type of MSD TBD 
+  \begin{itemize}
+	\item We extracted values of $\sigma$, $\alpha$ and $H$ for each solute
+	and then simulated 10000 sFBM trajectories of the same length as our MD
+	simulations, as described in Section~\ref{section:model_sFBM} of the Methods.
+	\item The final MSDs of the sFBM trajectories are compared to those 
+	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
+	\item The three sFBM parameters, calculated based on MD solute trajectories
 	are presented in Table~\ref{table:simulations}.
+	\item We would like to emphasize that we rely on the MD MSD values in order to
+	define trends in the total MSD, while the sFBM trajectories and parameter 
+	values allow us to speculate as to the reasons for the observed trends. 
+	\item There is a non-negligible amount of error in the calculation of 
+	each parameter which prevents us from reliably portraying our sFBM MSDs as
+	reduced	uncertainty MD MSDs.
+  \end{itemize}
+
+  Our simulated sFBM MSDs qualitatively reproduce the MD trends.
+  \begin{itemize}
+    \item sFBM generally lower
+    \item There are a few noticeable discrepancies.
+    \item We will discuss reasons for these as we proceed with the discussion.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{all_emsds.pdf}
+  \caption{}\label{fig:all_msds}
+  \end{figure}
 
@@
   \centering
-  \begin{tabular}{ccccc}
+  \begin{tabular}{cccc}
   \toprule
-  System & $\sigma$ ($nm$) & $\alpha$ & $H$ & Simulated MSD ($nm^2$)\\
+  System & $\sigma$ ($nm$) & $\alpha$ & $H$ \\
   \midrule
-  Methanol & 0.46 & 0.85 & 0.40 & 55.06 [49.26, 60.58] \\
-  Urea & 0.33 & 0.64 & 0.40 & 15.64 [14.08, 17.32] \\
-  Ethylene Glycol & 0.35 & 0.64 & 0.36 & 6.30 [5.69, 6.93] \\
-  Acetic Acid & 0.28 & 0.51 & 0.43 & 4.11 [3.66, 4.65] \\
-  Mercaptoethanol & 0.32 & 0.58 & 0.37 & 2.54 [2.16, 2.93] \\
-  Propylene Glycol & 0.26 & 0.50 & 0.43 & 1.94 [1.70, 2.17] \\
-  Ethanol & 0.32 & 0.55 & 0.26 & 1.29 [1.14, 1.43] \\
-  Propanol & 0.25 & 0.41 & 0.39 & 1.13 [1.01, 1.27] \\
-  Glycerol & 0.22 & 0.46 & 0.37 & 1.09 [0.98, 1.20] \\
-  Ethyl Acetate & 0.21 & 0.42 & 0.37 & 0.82 [0.74, 0.91] \\
-  Acetone & 0.23 & 0.44 & 0.34 & 0.80 [0.70, 0.88] \\
-  Dimethyl Sulfoxide & 0.25 & 0.47 & 0.29 & 0.74 [0.65, 0.82] \\
-  Tetrose & 0.22 & 0.43 & 0.20 & 0.68 [0.61, 0.75] \\
-  Acetamide & 0.27 & 0.52 & 0.21 & 0.56 [0.51, 0.64] \\
-  2,3-Dimercapto-1-propanol & 0.20 & 0.38 & 0.37 & 0.53 [0.47, 0.58] \\
-  Butanol & 0.19 & 0.41 & 0.33 & 0.42 [0.36, 0.49] \\
-  Propylene Carbonate & 0.19 & 0.38 & 0.29 & 0.30 [0.26, 0.34] \\
-  Tetrahydrofuran & 0.25 & 0.40 & 0.24 & 0.29 [0.25, 0.34] \\
-  Dimethyl Formamide & 0.20 & 0.39 & 0.27 & 0.27 [0.24, 0.31] \\
-  Ribose & 0.21 & 0.43 & 0.23 & 0.27 [0.24, 0.31] \\
+  Methanol & 0.46 & 0.85 & 0.40 \\
+  Urea & 0.33 & 0.64 & 0.40 \\
+  Ethylene Glycol & 0.35 & 0.64 & 0.36 \\
+  Acetic Acid & 0.28 & 0.51 & 0.44 \\
+  Mercaptoethanol & 0.30 & 0.54 & 0.26 \\
+  Ethanol & 0.32 & 0.55 & 0.25 \\
+  Propylene Glycol & 0.26 & 0.48 & 0.35 \\
+  Glycerol & 0.23 & 0.46 & 0.37 \\
+  Acetamide & 0.28 & 0.52 & 0.26 \\
+  Propanol & 0.25 & 0.41 & 0.35 \\
+  Acetone & 0.23 & 0.44 & 0.34 \\
+  Ethyl Acetate & 0.21 & 0.41 & 0.37 \\
+  Dimethyl Sulfoxide & 0.26 & 0.48 & 0.26 \\
+  Tetrose & 0.24 & 0.43 & 0.30 \\
+  Butanol & 0.19 & 0.41 & 0.33 \\
+  Dimethyl Formamide & 0.20 & 0.39 & 0.32 \\
+  2,3-Dimercapto-1-propanol & 0.20 & 0.37 & 0.35 \\
+  Ribose & 0.20 & 0.40 & 0.27 \\
+  Propylene Carbonate & 0.19 & 0.38 & 0.29 \\
+  Tetrahydrofuran & 0.24 & 0.39 & 0.16 \\
   \bottomrule
@@
 
-  It most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the simulated
+  It most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the
   simulated MSD values presented in Table~\ref{table:simulations}. 
@@
   	\item All of which contribute to an overall increase in the simulated MSD
-  \end{itemize}
-
-  Polar molecules generally exhibit a hop diffusion mechanism. 
-  \begin{itemize}
-	\item Each trajectory is characterized by a power law distribution of
-	dwell times between hops of random lengths from a Gaussian distribution.
   \end{itemize}

### 2019-01-30 Ben_Manuscripts/transport/figures/msd_table.py

@@ -1,41 +1,24 @@
 #!/usr/bin/env python
 
 import sqlite3 as sql
+import names
 
 connection = sql.connect("../../../timeseries/msd.db")
 crsr = connection.cursor()
-query = "SELECT name, sigma, alpha, hurst, python_MSD, python_MSD_CI_lower, python_MSD_CI_upper from msd ORDER BY python_MSD DESC"
+penalty = 0.25
+query = "SELECT name, sigma, alpha, hurst, python_MSD, python_MSD_CI_lower, python_MSD_CI_upper from msd WHERE penalty = %.2f ORDER BY python_MSD DESC" % penalty
 output = crsr.execute(query).fetchall()
 
-# dictionary of residue names and their corresponding chemical names as they will be dispalyed in the table
-res_to_name = {}
-res_to_name["ACN"] = "Acetamide"
-res_to_name["ACH"] = "Acetic Acid"
-res_to_name["ATO"] = "Acetone"
-res_to_name["BUT"] = "Butanol"
-res_to_name["DMF"] = "Dimethyl Formamide"
-res_to_name["DMS"] = "Dimethyl Sulfoxide"
-res_to_name["DMP"] = "2,3-Dimercapto-1-propanol"
-res_to_name["EAC"] = "Ethyl Acetate"
-res_to_name["ETH"] = "Ethanol"
-res_to_name["GCL"] = "Ethylene Glycol"
-res_to_name["GLY"] = "Glycerol"
-res_to_name["MET"] = "Methanol"
-res_to_name["PR"] = "Propanol"
-res_to_name["PCB"] = "Propylene Carbonate"
-res_to_name["PG"] = "Propylene Glycol"
-res_to_name["RIB"] = "Ribose"
-res_to_name["SOH"] = "Mercaptoethanol"
-res_to_name["TET"] = "Tetrose"
-res_to_name["THF"] = "Tetrahydrofuran"
-res_to_name["URE"] = "Urea"
-
 table = ""
-table += r"\begin{table}[h]" + "\n" + r"  \centering" + "\n" + r"  \begin{tabular}{ccccc}" + "\n" + r"  \toprule" + "\n"
-table += r"  System & $\sigma$ ($nm$) & $\alpha$ & $H$ & Simulated MSD ($nm^2$)\\" + "\n" + r"  \midrule" + "\n"
[…]

### 2019-01-30 HII/Scripts/gentop.py

@@ -29,7 +29,8 @@ class SystemTopology(object):
         :param gro: (str) coordinate file for which to create topology
         :param ff: (str) forcefield to use (default=gaff)
         """
-
+        print(gro)
+        exit()
         t = md.load(gro)  # load coordinate file
 
         self.script_location = os.path.realpath(os.path.join(os.getcwd(), os.path.dirname(__file__)))

### 2019-01-30 setup/gentop.py

@@ -3,6 +3,7 @@
 import argparse
 import mdtraj as md
 import os
+from LLC_Membranes.llclib import topology
 
 
 def initialize():
@@ -96,7 +97,8 @@ class SystemTopology(object):
             if i in self.ions:
                 natoms = 1
             else:
-                natoms = md.load('%s/%s.gro' % (self.top_location, i)).xyz.shape[1]  # number of atoms that make up a single residue of type i
+                natoms = topology.Residue(i).natoms
+                #natoms = md.load('%s/%s.gro' % (self.top_location, i)).xyz.shape[1]  # number of atoms that make up a single residue of type i
             residue_count[i] = residues.count(i) // natoms
 
         self.residues = unique_residues

### 2019-02-04 Ben_Manuscripts/transport/Outline.tex
outline edits and renaming

--- 2019-01-08 Ben_Manuscripts/transport/Outline.tex
@@
 
-  There is a broad range of water concentrations which will form a stable 
-  H\textsubscript{II} phase with Na-GA3C11. 
+  Stable H\textsubscript{II} phases, assembled with Na-GA3C11, can be formed
+  using a broad range of water concentrations.
   \begin{itemize}
-	\item In the literature this system is typically synthesized with close
-	to 10 wt \% water
+	\item In the literature, this system is typically synthesized with close
+	to 10 wt \% water \cite{smith_ordered_1997, zhou_new_2007}
     \item However, Resel et al. noted that the system is likely fully 
-	hydrated with less than 7 wt \% water.
+	hydrated with less than 7 wt \% water. \cite{resel_h2-phase_2000}
 	\item We decided to test two different levels of water content: 5 and 10 wt \%
@@
 
-  %MRS: may need to discuss the fact that the amount of water present in the tails may 
-  %MRS: or may not be experimentally consistent; but if we don't put it in, the results will 
-  %MRS: not be thermodynamically consistent, which will give issues with measurements and calculations.
-  %MRS2: hopefully, some experiments could let us know about different diffusion regimes . . . 
   We observed that water partitions into the tail region of our system and therefore
@@
 	\item At each insertion point we placed a randomly oriented solute molecule
-	then ran a short energy minimzation.
+	then ran a short energy minimization.
 	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
 	pressure control
-	\item We collected transport data using long simulations, on the order of
-	1 microsecond
-	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
+	\item We collected transport data using 1 $\mu$s simulations
   \end{itemize}
 
-  \subsubsection*{Modeling the Continuous Time Random Walk}\label{method:CTRW}
-
-  A continuous time random walk (CTRW) is a stochastic anomalous diffusion
-  process characterized by a distribution of hop lengths and dwell times.
-  \begin{itemize}
-	\item The MSD for an anomalous diffusion process is of the form
-	\begin{equation} 
-	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
-	\label{eqn:msd_form}
-	\end{equation} 
-	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
-	generalized diffusion coefficient. 
-	\item A value of $\alpha < 1$ indicates a subdiffusive process.
-	\item Subdiffusive, non-ergodic processes with uncorrelated steps distinguish 
-	a CTRW from other anomalous subdiffusive process such as fractional brownian motion 
-	and random walks on a fractal.~\cite{meroz_toolbox_2015}
-	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
-  \end{itemize}
-
-  We obtained maximum likelihood estimates (MLE) of the parameters used to fit our
-  emperical dwell and hop length distributions to analytical functions.
-  \begin{itemize}
-	\item We used the \texttt{ruptures} python package in order to identify
-	breakpoints in solute trajectories. (See Supporting Information for more
-	details on chosen parameters. i.e. type of cost function, cost function penalty
-	tolerance, number of dimensions used)
-	\item The corresponding hop lengths and dwell times between break points were 
-	used to construct emperical distributions.
-	\item For solutes in our system the distribution of hop lengths is
-	well-represented by a Gaussian distribution (Which has been often used in
-	literature)
-	\item The maximum likelihood estimate of Gaussian parameters is given simply
-	by the mean and standard deviation of the emperical data.
-	~\cite{metzler_random_2000,metzler_anomalous_2014,neusius_subdiffusion_2009} 
-	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
-	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
-	\item Because we are limited to taking measurements at discrete values
-	dictated by the output frequency of our simulation trajectories, we fit the
-	emperical dwell times to a discrete power law distribution whose maximum
-	likelihood $\alpha$ parameter we calculated by maximizing the following
-	likelihood function: 
-        \begin{equation}
-	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
-	\beta\sum_{i=1}^{n} \text{ln}~x_i 
-	\label{eqn:powelaw_likelihood}
-	\end{equation}
-	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
-	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
-	where $x_{min}$ is the smallest measured value of
-	$x_i$.~\cite{clauset_power-law_2009} 
-	%\item Incorporates effects of `aging' since it samples long dwell times
-  \end{itemize}
-
-  %BJC: not sure following explanation is necessary. Could put thesis statement
-  % in previous paragraph.
-  We generated distributions of parameters for the dwell time and hop length
-  distributions using statistical bootstrapping.
-  \begin{itemize}
-	\item For each type of distribution, we randomly selected $n$ data points from the emperical
-	distribution with replacement.
-	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
-  \end{itemize}
-
-%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
-%  magnitude longer than our molecular simulations.
-  We simulated trajectories order of magnitude longer than our molecular simulations. 
-  \begin{itemize}
-	\item We constructed 10000, 10000 timestep trajectories by generating
-	sequences of dwell times and hop lengths randomly sampled from the appropriate
-	distributions.
-	\item For each trajectory, the parameters used to define each distribution were
-	randomly drawn from the bootstrapped parameter distributions.
-	\item We randomly sample Gaussian hop lengths using the
-	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
-	\item We randomly sampled dwell times from a discrete power law
-	distribution based on the reccomendations of Clauset et
-	al.~\cite{clauset_power-law_2009}: 
-	\begin{equation}
-	x = \lfloor
-	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
-	\label{eqn:discrete_powerlaw_draws}
-	\end{equation}
-	where $r$ is randomly drawn from a uniform distribution which we simulated
-	with \texttt{numpy.random.uniform}.
-	\item We found that thermal noise does not significantly influence the MSD and
-	therefore did not add any noise to the simulated trajectories. (See supporting info)
-  \end{itemize}
-
-  We calculated both the ensemble-averaged and time-averaged mean squared displacements (MSDs)
-  of the simulated trajectories.
-  \begin{itemize}
-	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
-	position ~\cite{meroz_toolbox_2015} and can be written as
-	\begin{equation}
-	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
-	\label{eqn:ensemble_msd}
-	\end{equation}
-	\item The average MSD calculated in this way recovers the form of
-	Equation~\ref{eqn:msd_form}. 
-	\item The time-averaged MSD measures the displacement between all possible time lags
-	and can be written as
-	\begin{equation}
-	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}{T - \tau} (x(t + \tau) - x(t))^2 dt
-	\end{equation}
-	where $\tau$ is the time lage and T is the length of the
-	trajectory~\cite{meroz_toolbox_2015}. 
-	\item The time-averaged MSD becomes linear in our simulations,
-	therefore we can fit a line to its slope in order to estimate the macroscopic
-	diffusivity of the particle.
-	%BJC: this needs more justification. Not many people have done it
-	%BJC: could also not report them as diffusivities. Comparison of total MSD
-	% should give same information
-	% Linear region probably exists because dwell times on the order of large lag times
-	% become negligible
-  \end{itemize}
-
-  We fixed the length of each simulated trajectory so that we could compare the total
-  MSD between different solutes without the influence of the ageing phenomenon.
-  \begin{item}
-	\item Ageing is defined by the tendency of the average MSD to decrease
-	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
-	\item The maximum measured dwell time can be no longer than the total length
-	of a simulated trajectory. 
-	\item As measurement time or trajectory length is increased, longer dwell times
-	are incorporated into the calculation, lowering the average MSD. (See supporting
-	info for demonstration)
-	\item We can achieve consistent total MSDs with low uncertainty for
-	simulated trajectories created with a given set of parameters if we fix the
-	trajectory length (as opposed to total number of steps).  
-  \end{item}
+%  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}
+%
+%  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
+%  behavior, a type of anomalous diffusion. 
+%  \begin{itemize}
+%  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
+%  	does not grow linearly with time, rather it is of the form:
+%	\begin{equation} 
+%	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
+%	\label{eqn:msd_form}
+%	\end{equation} 
+%	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
+%	generalized diffusion coefficient.
+%	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
+%	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
+%	motion respectively.
+%  \end{itemize}
+%
+%  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
+%  of the simulated trajectories.
+%  \begin{itemize}
+%	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
+%	position~\cite{meroz_toolbox_2015} and can be written as
+%	\begin{equation}
+%	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
+%	\label{eqn:ensemble_msd}
+%	\end{equation}
+%%	\item The average MSD calculated in this way recovers the form of
+%%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
+%	\item The time-averaged MSD measures the displacement between all possible time lags
+%	and can be written as
+%	\begin{equation}
+%	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
+%	\end{equation}
+%	where $\tau$ is the time lag and T is the length of the
+%	trajectory~\cite{meroz_toolbox_2015}. 
+%%	\item The time-averaged MSD becomes linear in our simulations,
+%%	therefore we can fit a line to its slope in order to estimate the macroscopic
+%%	diffusivity of the particle.
+%	%BJC: this needs more justification. Not many people have done it
+%	%BJC: could also not report them as diffusivities. Comparison of total MSD
+%	% should give same information
+%	% Linear region probably exists because dwell times on the order of large lag times
+%	% become negligible
+%  \end{itemize}
+%  
+%  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
+%  continuous time random walks (CTRW), fractional Brownian motion (FBM) and
+%  random walks on fractals (RWF).\cite{meroz_toolbox_2015}
+%  \begin{itemize}
+%    \item FBM is common in crowded, viscoelastic environments where each step comes 
+%    from a Gaussian distribution but is anti-correlated to its previous 
+%    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
+%    \item A CTRW is characterized by a distribution of hop lengths and 
+%    dwell times, where each each step is characterized by independent random draws from 
+%    each distribution.\cite{montroll_random_1965,morrin_three_2018}
+%    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
+%    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
+%    \item The processes described above can happen alone or in combination.  	
+%  \end{itemize}
+%  
+%  \noindent We believe that solutes in the system studied here exhibit subordinated 
+%  fractional Brownian motion (sFBM) where the parent process is FBM and the 
+%  leading process is a CTRW. 
+%  \begin{itemize}
+%  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
+%  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
+%  	\item We also observe non-stationary $z$-coordinate traces of each solute's
+%  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
+%  	\item For a pure CTRW, the time-averaged MSD should be linear.
+%  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
+%  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
+%  	information), which suggests that there is another underlying subdiffusive mechanism.
+%  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
+%  	\item Given the viscoelastic nature of the monomers in our system, we believe
+%  	the hop lengths can be modeled with FBM. 
+% 	\item For subordinated FBM, it can be shown that
+%  	\begin{equation}
+%  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
+%  	\end{equation}
+%  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
+%  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
+%  \end{itemize}
+%
+%  \noindent We can characterize a CTRW process using the parameters which describe its
+%  dwell time and hop length distribution.
+%  \begin{itemize}
+%	\item We used the \texttt{ruptures} python package in order to identify
+%	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
+%	details on chosen parameters. i.e. type of cost function, cost function penalty
+%	tolerance, number of dimensions used)
+%	\item The corresponding hop lengths and dwell times between break points were 
+%	used to construct empirical distributions.
+%	\item For solutes in our system, the distribution of hop lengths is
+%	well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
+%	metzler_anomalous_2014,neusius_subdiffusion_2009}
+%	\item We are most interested in the standard deviation, $\sigma$, of the 
+%	hop length distribution.
+%	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
+%	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
+%	\item Because we are limited to taking measurements at discrete values
+%	dictated by the output frequency of our simulation trajectories, we fit the
+%	empirical dwell times to a discrete power law distribution whose maximum
+%	likelihood $\alpha$ parameter we calculated by maximizing the following
+%	likelihood function: 
+%        \begin{equation}
+%	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
+%	\beta\sum_{i=1}^{n} \text{ln}~x_i 
+%	\label{eqn:powerlaw_likelihood}
+%	\end{equation}
+%	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
+%	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
+%	where $x_{min}$ is the smallest measured value of
+%	$x_i$.~\cite{clauset_power-law_2009} 
+%	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
+%	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
+%  \end{itemize}
+%  
+%  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
+%  $H = \beta/2$.
+%  \begin{itemize}
+%  	\item Brownian motion is recovered for $H = 0.5$
+%	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
+%    \begin{equation}
+%	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
+%	\label{eqn:autocovariance}
+%	\end{equation}
+%	where $k$ is the number of increments between hops.
+%	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
+%	to the empirically measured autocovariance function.
+%	\item We used statistical bootstrapping to generate a distribution of $H$ 
+%	values. %BJC: can provide more detail in supporting or just reference python script
+%  \end{itemize}
+%
+%%  We generated distributions of parameters for the dwell time and hop length
+%%  distributions using statistical bootstrapping.
+%%  \begin{itemize}
+%%	\item For each type of distribution, we randomly selected $n$ data points from the empirical
+%%	distribution with replacement.
+%%	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
+%%  \end{itemize} 
+%
+%%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
+%%  magnitude longer than our molecular simulations.
+%  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
+%  \begin{itemize}
+%	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
+%	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
+%	distributions.
+%	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
+%	the last data point so that the total time exactly equaled 1 $\mu$s. 
+%    \item Valid comparisons are only possible between fixed length sFBM simulations. The
+%    power law dwell time behavior gives rise to the aging phenomenon, embodied by
+%    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
+%    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
+%% Following probably better suited for supporting information, if included at all
+%%	\item We randomly sample Gaussian hop lengths using the
+%%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
+%%	\item We randomly sampled dwell times from a discrete power law
+%%	distribution based on the recommendations of Clauset et
+%%	al.~\cite{clauset_power-law_2009}: 
+%%	\begin{equation}
+%%	x = \lfloor
+%%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
+%%	\label{eqn:discrete_powerlaw_draws}
+%%	\end{equation}
+%%	where $r$ is randomly drawn from a uniform distribution which we simulated
+%%	with \texttt{numpy.random.uniform}.
+%%	\item We found that thermal noise does not significantly influence the MSD and
+%%	therefore did not add any noise to the simulated trajectories. (See supporting info)
+%  \end{itemize}
+%
+%%BJC: probably don't need to explain this in great detail
+%%  \noindent We fixed the length of each simulated trajectory so that we could compare the total
+%%  MSD between different solutes without the influence of the ageing phenomenon.
+%%  \begin{itemize}
+%%	\item Ageing is defined by the tendency of the average MSD to decrease
+%%	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
+%%	\item The maximum measured dwell time can be no longer than the total length
+%%	of a simulated trajectory. 
+%%	\item As measurement time or trajectory length is increased, longer dwell times
+%%	are incorporated into the calculation, lowering the average MSD. (See supporting
+%%	info for demonstration)
+%%	\item We can achieve consistent total MSDs with low uncertainty for
+%%	simulated trajectories created with a given set of parameters if we fix the
+%%	trajectory length (as opposed to total number of steps).  
+%%  \end{itemize}
 
@@
   \begin{itemize}
-  	\item For each frame, we counted the identites and number of
+  	\item For each frame, we counted the identities and number of
   	coordinated molecules to a given solute based on a distance cut-off. 
@@
 
-  \subsection{Experimental}
-  % BJC: For Greg to write if things work out
-
   \section{Results and Discussion}
 
-  \subsection{Simulated Predictions}\label{section:D_macro}
+  \subsection{Governing Mechanisms}\label{section:mechanism_overview}
 
-  Polar molecules generally exhibit a hop diffusion mechanism. 
+  % BJC: seems right to summarize overarching mechanisms observed first  
+  On the timescales simulated in our study, solutes exhibit subdiffusive
+  transport behavior as evidenced by their sublinear MSD curves. 
   \begin{itemize}  
-	\item Each trajectory is characterized by a power law distribution of
-	dwell times between hops of random lengths from a Gaussian distribution.
+	\item As an example, the MSD curve for ethanol is plotted in 
+	Figure~\ref{fig:example_msd}.
   \end{itemize}
 
-  % BJC: figure with selected trajectories for each molecule.
-
-  We fit a CTRW model (see Section~\ref{method:CTRW}) to these 
-  trajectories and predicted macroscopic diffusion coefficients which are
-  presented in Table TBD.
+  \noindent All solutes exhibit hop diffusion, characteristic of a continuous time random walk.
   \begin{itemize}
-	\item We confirmed that our molecules exhibit anomalous diffusion
-	by fitting a power law to the MSD curve. The exponent is less than
-	1, indicative of anomalous subdiffusion.
-	\item We used the decision making process given by Meroz and Sokolov
-	in order to identify the appropriate subdiffusion model to use 
-	based on our time series (See Section S-TBD of the Supporting info for
-	more details).
-	\item The motion of the solutes is non-ergodic and the steps are
-	uncorrelated which tells us the system is likely well-described
-	by a CTRW. 
+  	\item Figure~\ref{fig:example_ztraces} shows the $z$-coordinate versus time of
+  	3 representative ethanol centers of mass.
+  	\item There are clear periods of entrapment separated by relatively large hops.
+  	\item The length of entrapment follows a power law distribution 
+  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
+  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
+  	\item Power law distributed dwell times are responsible for the ageing phenomenon
+  	which causes the MSD curve to decrease with increasing measurement time as longer
+  	dwell times get sampled.
   \end{itemize}
 
-  % BJC: table with finalized diffusion coefficients
+  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
+  \begin{itemize}
+  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
+  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Better word?
+  	\item The negative autocovariance at low values of k indicates anti-correlation
+  	between steps. 
+  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
+  	decay to zero immediately.
+  	\item Although the autocovariance function is relatively noise, due to the somewhat small
+  	number of hops observed over the course of each solute trajectory, there is the least 
+  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
+  	all solutes molecules.
+  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
+  	motion where the leading process is a CTRW with hops that are dictated by the parent
+  	process, FBM.
+  	\item Future publications will focus on modeling the solute's transport characteristics
+  	with an sFBM model
+  \end{itemize}
+
+% BJC: first iteration of figure after this before I decided to include a hop length and dwell time distribution
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=\textwidth]{msd_ztrace_acf.pdf}
+%  \caption{}\label{fig:msd_ztrace_acf}
+%  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\linewidth]{example_msd.pdf}
+  \caption{}\label{fig:example_msd}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\linewidth]{example_ztraces.pdf}
+  \caption{}\label{fig:example_ztraces}
+  \end{subfigure}
+  \par\medskip
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\linewidth]{example_powerlaw.pdf}
+  \caption{}\label{fig:example_powerlaw}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\linewidth]{example_hop_dist.pdf}
+  \caption{}\label{fig:example_hop_dist}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\linewidth]{example_autocovariance.pdf}
+  \caption{}\label{fig:example_autocovariance}
+  \end{subfigure}
+  \caption{All solutes show subdiffusive transport behavior inside the membrane's
+  nanopores, similar to that exhibited by ethanol. (a) The time-averaged MSD of 
+  ethanol is not linear which suggests transport is governed by an anomalous 
+  subdiffusion process. (b) The $z$-coordinate trace of 3 representative ethanol
+  COMs shows clear periods of entrapment separated by hops. (c) The distribution
+  of dwell times follows a power law. (d) The distribution of hop lengths appears
+  Gaussian. (e) Hops are anti-correlated to their previous hop as indicated by the
+  negative value of the autocovariance function at $k$ = 1.}\label{fig:examples}
+  \end{figure}
+
+  % BJC: would it be better to report as a fraction of water MSD?
+  \noindent We calculated the time-averaged MSD of each solute in the set over the
+  course of 1 $\mu$s MD simulations. 
+  \begin{itemize}
+    \item Because the MSDs are non-linear and because of the ageing phenomenon, we
+    did not attempt to calculate a diffusion constant as one might for a Brownian
+    particle with a linear MSD.
+	\item Instead, the values plotted in Figure~\ref{fig:all_msds} represent the
+	average MSD of each solute after a 400 ns time lag.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{all_tamsds.pdf}
+  \caption{}\label{fig:all_msds}
+  \end{figure}
+
+  \noindent The MSDs in Figure~\ref{fig:all_msds} are a strong function of two solute 
+  trapping mechanisms. % by which solutes become trapped.
+  \begin{itemize}
+  	\item Solutes that are hydrogen bond donors can be stabilized through hydrogen bonds
+  	with one of the five oxygen atoms attached to each monomer head group. 
+  	\item In a separate interaction, solutes can become kinetically trapped between 
+  	monomer head groups.
+  	\item Generally, both mechanisms affect each solute to varying degrees.
+  \end{itemize}
+
+  %BJC: somewhere need to say why solutes preferentially hbond with carboxylate groups -- is this real
+
+  \noindent A solute's size, shape, and polarity dictate the degree to which they 
+  are influenced by each entrapment mechanism.
+  \begin{itemize}
+    \item In general, solutes can move fastest in the pore center, where
+    there is comparatively little resistance to diffusion.
+%    \item The smallest molecular weight solutes move fastest.
+    \item Low molecular weight, highly water-soluble, hydrogen bond donating molecules spend the most time
+    in the pore center where they are slowed down primarily by hydrogen bonds
+    with monomer carboxylate groups.
+    %BJC: this isn't fully accurate yet. Need to come back to this
+    \item Solutes that cannot donate hydrogen bonds, or are less miscible in water, 
+    tend to partition into the head group region where entrapment occurs. Most of
+    the anti-correlated motion occurs here.
+    \item The inverse relationship between solute size and mobility is disrupted
+    by solutes' preference for water. 
+    \item We observe low MW solutes with lower-than-expected MSDs because they
+    spend more time trapped between monomer head groups due to low water
+    solubility.
+    \item Small, planar molecules exhibit some of the shortest MSDs because
+
+  	\item The well-established trend of decreasing solute mobility with 
+  	size is not defied here, however 
+  	\item Additionally, planar molecules are prone to exhibiting similar
+  	trapping behavior, even for large molecules whose similar sized, but flexible
+  	counterparts exhibit faster diffusion.  %BJC: this is unproven
+  	\item The polarity of solutes also influences a solute's ability to stay in
+  	the pore center. Highly polar molecules tend to spend more time in the pore center,
+  	while those with hydrophobic character tend to spend more time in the head group
+  	region.
+  	\item Finally, the ability to hydrogen bond offers a second trapping mechanism. 
+  	Solutes that are hydrogen bond donors can donate hydrogen atoms to
+  	any of the 5 oxygen atoms located on the monomer head groups. Increasing the 
+  	number of hydrogen bond donating groups increases the solute's polarity causing
+  	solutes to spend more time in the pore centers, but the effect can be countered
+  	by excessive trapping if there are many hydrogen bonds being formed.
+  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
+  	mechanisms, with anticorrelated hops between each period of immobility due to 
+  	obstructions.
+  \end{itemize}
+
+  We will revisit these observations in the the context of specific groups of 
+  molecules in the discussion that follows.
+
+%  We will explore these factors in greater detail in the context of 
+%  specific groups of molecules in the discussion that follows.
+
+  \subsection{Mean Squared Displacement Predictions}\label{section:msd_predictions}
+
+  %BJC: focus on MD MSD results
 
@@
   \bibliographystyle{ieeetr}
-  \bibliography{Transport}
+  \bibliography{transport}
 

### 2019-02-04 llclib/physical.py

@@ -617,6 +617,9 @@ def partition(com, pore_centers, r, buffer=0, unitcell=None, npores=4, spline=Fa
     :type unitcell: numpy.ndarray (nT, 3, 3)
     :type npores: int
     :type spline: bool
+
+    :return part: boolean numpy array with shape (nT, com.shape[1]) where True indicates a center of mass that is
+    inside the pore region
     """
 
     nT = com.shape[0]

### 2019-02-05 Ben_Manuscripts/transport/Outline.tex
Outline updates

@@
 
-  \subsection{Governing Mechanisms}\label{section:mechanism_overview}
+  \subsection*{Governing Mechanisms}\label{section:mechanism_overview}
 
@@
   % BJC: would it be better to report as a fraction of water MSD?
+  % BJC: need MSDs of 5 wt % systems here too. Can narrow to study of 10 wt % systems after
   \noindent We calculated the time-averaged MSD of each solute in the set over the
@@
   \end{itemize}
+
+%  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}
+%
+%  Solutes in systems with lower water content exhibit lower diffusion coefficients.
+%  \begin{itemize}
+%	\item Pores are more crowded when there is less water (show RDFs of each)
+%	\item Not a linear function of pore size - radius increase by x, D increases by y
+%	\item Larger influence on bigger molecules
+%  \end{itemize}
 
@@
   	\item In a separate interaction, solutes can become kinetically trapped between 
-  	monomer head groups.
+  	monomer head groups. These interactions likely lead to the observed anti-correlated
+  	hopping	behavior.
   	\item Generally, both mechanisms affect each solute to varying degrees.
@@
 
-  \noindent A solute's size, shape, and polarity dictate the degree to which they 
-  are influenced by each entrapment mechanism.
+  %BJC: This will need updating once all the rest of outline is written.
+  \noindent The degree to which solutes are influenced by each entrapment mechanism
+  is a complex function of a solute's size, shape, and polarity.
   \begin{itemize}
@@
     there is comparatively little resistance to diffusion.
-%    \item The smallest molecular weight solutes move fastest.
-    \item Low molecular weight, highly water-soluble, hydrogen bond donating molecules spend the most time
-    in the pore center where they are slowed down primarily by hydrogen bonds
-    with monomer carboxylate groups.
-    %BJC: this isn't fully accurate yet. Need to come back to this
-    \item Solutes that cannot donate hydrogen bonds, or are less miscible in water, 
-    tend to partition into the head group region where entrapment occurs. Most of
-    the anti-correlated motion occurs here.
-    \item The inverse relationship between solute size and mobility is disrupted
-    by solutes' preference for water. 
+	\item The 5 fastest solutes in our study have a low molecular weight and
+	spend a significant amount of time in the pore center. They are only slowed
+	by hydrogen bonds with monomer carboxylate groups.
+	\item Bulky solutes with many hydrogen bond donating groups, like glycerol,
+	spend most of their time in the pore center, but their large size combined
+	with a higher solute-head group hydrogen bond frequency, makes their dynamics slow. 
+    \item Solutes with high hydrophobic character tend to partition into the 
+    head group region where entrapment occurs.
     \item We observe low MW solutes with lower-than-expected MSDs because they
@@
     solubility.
-    \item Small, planar molecules exhibit some of the shortest MSDs because
-
-  	\item The well-established trend of decreasing solute mobility with 
-  	size is not defied here, however 
-  	\item Additionally, planar molecules are prone to exhibiting similar
-  	trapping behavior, even for large molecules whose similar sized, but flexible
-  	counterparts exhibit faster diffusion.  %BJC: this is unproven
-  	\item The polarity of solutes also influences a solute's ability to stay in
-  	the pore center. Highly polar molecules tend to spend more time in the pore center,
-  	while those with hydrophobic character tend to spend more time in the head group
-  	region.
-  	\item Finally, the ability to hydrogen bond offers a second trapping mechanism. 
-  	Solutes that are hydrogen bond donors can donate hydrogen atoms to
-  	any of the 5 oxygen atoms located on the monomer head groups. Increasing the 
-  	number of hydrogen bond donating groups increases the solute's polarity causing
-  	solutes to spend more time in the pore centers, but the effect can be countered
-  	by excessive trapping if there are many hydrogen bonds being formed.
+    \item Small, planar molecules like acetone exhibit some of the slowest MSDs.
+    Their flat geometry and small size makes it easy for them to get lodged deep
+    between head groups.
   	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
@@
 
-  \subsection{Mean Squared Displacement Predictions}\label{section:msd_predictions}
+  \subsection*{Transport of Water}
 
-  %BJC: focus on MD MSD results
+  Water molecules also exhibit hop diffusion.
 
-  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}
-
-  Solutes in systems with lower water content exhibit lower diffusion coefficients.
-  \begin{itemize}
-	\item Pores are more crowded when there is less water (show RDFs of each)
-	\item Not a linear function of pore size - radius increase by x, D increases by y
-	\item Larger influence on bigger molecules
-  \end{itemize}
-
-  \subsubsection{Experimental Measurements}
-
-  % For Greg
-
-  \subsection{Transport Mechanisms}
-
-  In order to truly understand the molecular origins of the macroscopic
-  diffusion coefficients in Section~\ref{section:D_macro}, we studied the
-  microscopic interactions between solutes and the membrane that lead to the
-  observed dwell time and hop distributions.
-  \begin{itemize}
-	\item We studied the radial distribution functions of solutes as a
-	function of distance from the pore center
-	\item We looked at hydrogen bonding patterns
-	\item Coordination numbers
-	\item Order parameters
-  \end{itemize}
-
-  The radial distribution function of each solute studied is shown in 
-  Figure TBD.
-
-  \subsubsection*{Transport of Water}
-
-  All water molecules exhibit hop diffusion.
+  The overwhelming number of water molecules reduces
 
@@
 
-  \subsubsection*{Transport of Alcohols}
+  \subsection*{Transport of Simple Alcohols}
 
-  The hydroxyl functional group of alcohol molecules is a hydrogen bond donor
-  and prefers to donate it's hydrogen to more strongly polarized carboxylate head
-  groups.
-
-  As alcohol groups increase in hydrophobic character, they are more inclined
-  to stick to the outside edges of the pore. 
+  The MSD of methanol, ethanol, propanol and butanol descends in order of 
+  their molecular weight, however, methanol travels faster than expected.  %BJC: find approximate relationship between MW and mobility
   \begin{itemize}  
-	\item The alkane tails prefer to stay at the edges of the pore.
-	\item Radial distribution functions show peaks at pore edges, however
-	smaller alcohols have high densities near the pore center. 
-	\item They tend to get trapped between monomers and closer to 
-	the tail region. 
-	\item The entrapment is further stabilized by hydrogen bonds with
-	ether oxygens connecting the monomer's alkane tails to the head groups.
-	%TODO: quantify h-bonds with ether oxygens and carbonyl oxygens
+    \item The radial distribution as a function of distance from the pore center
+    for each alcohol is plotted in Figure~\ref{fig:simple_alcohol_rdf}.
+    \item On average, the density of methanol in the pore center is only slightly
+    less than the density near the head groups.
+    \item All other alcohol molecules are concentrated in the head group region.
   \end{itemize}
 
-  The diffusion coefficient of simple alcohols increases as the length of 
-  the alkane chain increases.
+  All simple alcohols participate in a similar number of hydrogen bonding interactions
+  with the monomer head groups , but with varying preference towards hydrogen bonds with
+  the monomer carboxylate oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds}).
   \begin{itemize}
-	\item The dwell times increase as the oily tails become more
-	entrapped in monomer tails.
+  	\item If all 5 hydrogen bonding acceptor sites on the monomer head groups were equal,
+  	we would expect the ratio of the number of hydrogen bonds between solutes and the two 
+  	carboxylate oxygen atoms to the number of hydrogen bonds between solutes and the three
+  	ether groups to be 2/3. 
+  	\item Clearly there is a preference towards hydrogen bonding with the carboxylate 
+  	oxygen atoms for all solutes.
+  	\item This is largely due to the more highly crowded environment surrounding the ether
+  	oxygen atoms.
+  	\item Butanol shows the largest preference towards hydrogen bonds with carboxylate 
+  	head groups.
+  	\item The radial distribution function of atoms located at opposite ends of butanol
+  	shows that, on average, oxygen atoms are situated 0.25 nm closer to the pore centers
+  	than the distal carbon.
+  	\item This suggests that alcohols tend to orient themselves like the liquid crystal 
+  	monomers, with hydrophilic components point towards the pore centers.
   \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
+  \caption{}\label{fig:simple_alcohol_rdf}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
+  \caption{}\label{fig:simple_alcohol_hbonds}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing 
+  \caption{}\label{fig:butanol_CO}
+  \end{subfigure}
+  \caption{(a) The radial distribution functions of each simple alcohol shows a maximum close
+  to the highest density of monomer head groups (dashed line, normalized for easier visual
+  comparison). Methanol spends the largest proportion of time, relative to the other alcohols,
+  near the pore center, which may help explain its fast dynamics. (b) Despite relatively little
+  difference in the total number of hydrogen bond occurences, a given alcohol's preference
+  towards hydrogen bonds with the carboxylate groups increases with molecule size. (c) The average
+  location of butanol's oxygen atom is significantly closer to the pore center than its most distal
+  carbon atom, suggesting that the molecule is oriented with hydrophobic tails pointing away from
+  the pore center.}\label{fig:simple_alcohols}
+  \end{figure}
+
+  \subsection*{Transport of Diols and Triols}
 
@@
 
-  \subsubsection*{Transport of Acetone}
+  \subsection*{Transport of Sugars}
+
+  \subsection*{Transport of Ketone-like Solutes}
 
@@
 
-  \subsubsection*{Transport of Acetic Acid}
+  \subsection*{Transport of Acetic Acid}
 
@@
 
-  \subsubsection*{Transport of Ions} % probably just sodium
+  \subsection*{Transport of Ions} % probably just sodium
 

### 2019-02-15 Ben_Manuscripts/transport/Outline.tex
Lots of plotting functions and updates to outline

@@
     particle with a linear MSD.
-	\item Instead, the values plotted in Figure~\ref{fig:all_msds} represent the
+	\item Instead, the MSD values plotted in Figure~\ref{fig:all_msds} represent the
 	average MSD of each solute after a 400 ns time lag.
@@
   \centering
-  \includegraphics[width=\textwidth]{all_tamsds.pdf}
+  \includegraphics[width=\textwidth]{all_tamsds.pdf}  % include bar plot of MW to show it's non-monotonic
   \caption{}\label{fig:all_msds}
   \end{figure}
+
+  \noindent The MSDs are not a monotonic function of solute molecular weight.
+  \begin{itemize}
+  	\item We plotted the solute molecular weights alongside their MSDs in Figure~\ref{fig:all_msds}.
+  	\item Transport is clearly affected by factors other than molecular weight. 
+  	\item Tetrose, our third heaviest solute, has an MSD higher than more than half of
+  	all solutes studied. 
+  	\item The three slowest solutes have lower molecular weights than 8 faster solutes.
+  \end{itemize}
 
@@
   All simple alcohols participate in a similar number of hydrogen bonding interactions
-  with the monomer head groups , but with varying preference towards hydrogen bonds with
+  with the monomer head groups, but with varying preference towards hydrogen bonds with
   the monomer carboxylate oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds}).
@@
   	ether groups to be 2/3. 
-  	\item Clearly there is a preference towards hydrogen bonding with the carboxylate 
-  	oxygen atoms for all solutes.
+  	\item There is a clear preference towards hydrogen bonding with the carboxylate 
+  	oxygen atoms for all simple alcohols.
   	\item This is largely due to the more highly crowded environment surrounding the ether
@@
   	shows that, on average, oxygen atoms are situated 0.25 nm closer to the pore centers
-  	than the distal carbon.
+  	than the distal carbon atoms.
   	\item This suggests that alcohols tend to orient themselves like the liquid crystal 
@@
   \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing 
+  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing butanol with highlighted O and C
   \caption{}\label{fig:butanol_CO}
@@
 
-  \subsection*{Transport of Diols and Triols}
+  \subsection*{Transport of Diols, Triols and Sugars}  % polyols instead of sugars?
 
-  Ethylene glycol, a diol, has two hydrogen bond donor groups.
+  Transport is both facilitated and hindered by additional solute hydroxyl groups.
   \begin{itemize}
-	\item Can hydrogen bond with same moeity.
-	\item Can hydrogen bond with different moeities in the same 
-	vicinity. 
-	\item Dwell times tend to be shorter. If one hydroxyl group is bound
-	with a hydrogen bond, the other unbound hydroxyl group may form a hydrogen bond
-	elsewhere and effectively pull the other bound hydroxyl group along with it. 
+    \item Extra hydroxyl groups cause solutes to favor the water-rich pore region
+    where there is the least hindrance to movement.
+    \item However, these extra hydroxyl groups facilitate a larger number of 
+    hydrogen bond interactions that work to hold solutes in place.
+    \item At the same time, solute molecular weight increases, which inherently
+    causes them to move more slowly.
+    \item Ethylene glycol, the fastest solute in this grouping (and second fastest
+    overall), obtains the best balance of both effects.
   \end{itemize}
 
-  \subsection*{Transport of Sugars}
+  The number of hydrogen bonding interactions between solutes and head groups
+  increases with the number of solute hydroxyl groups.
+  \begin{itemize}
+    \item These solutes frequently undergo simultaneous hydrogen bond interactions as
+    shown in Figure~\ref{fig:multi_hbonds}. 
+    \item For example, both hydroxyl groups of ethylene glycol can undergo hydrogen
+    bonds with different hydrogen bond acceptors at the same time.
+    \item In some cases, all 4 hydroxyl groups of ribose are hydrogen bonded to monomer
+    head groups simultaneously.
+%  	\item Simple alcohols, containing only one hydroxyl group, hydrogen bond
+%  	with head groups about 20 \% of the time. % BJC: I have a figure showing the average number of hydrogen bonds per solute
+  \end{itemize}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=\linewidth]{multi_hbonds.pdf}
+  \caption{The number of hydrogen bond interactions between solutes and monomers increases
+  as solutes gain additional hydroxyl groups. Multiple hydroxyl groups within a solute often
+  hydrogen bond in different locations simultaneously. Occasionally, all four hydroxyl groups
+  of Ribose (n = 4) are involved in a hydrogen bond interaction at the same time.}\label{fig:multi_hbonds}
+  \end{figure}
+
+  Between the two diols, ethylene glycol moves significantly faster than propylene glycol
+  due to propylene glycol's affinty for the monomer head groups.  
+  \begin{itemize}
+  	\item The distribution of each solute's dwell time and hop length distributions shows that
+  	ethylene glycol has shorter dwell times and longer hop lengths, which combine to create a 
+  	relatively fast MSD. 
+    \item Both diols have comparable densities close to the pore center, however propylene glycol's
+    density has a large peak near the monomer head groups relative to ethylene glycol. 
+    \item Combined with an increase in molecular weight, the addition of a single methyl group
+    increases the molecule's hydophobic character and causes propylene glycol to favor positions
+    near monomer head groups.
+    \item This causes propylene glycol to form more highly stablized hydrogen bonds with
+    carboxylate groups, explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
+    % BJC: could plot dwell time as a function of radial position (show that dwells are longest when PG
+    % is hbonding to head groups
+  \end{itemize}
+
+  Solutes with three or more hydroxyl groups have the highest density
+  at the pore center which contributes to overall faster than expected transport.
+  \begin{itemize}
+  	\item These molecules are highly water soluble but relatively large
+  	\item They can easily hydrogen bond in multiple locations.
+  	\item Their large size and high hydrogen bonding capability prevents them
+  	from have larger MSDs.
+  \end{itemize}
+
+  % BJC: Euclidean distance between simultaneous h-bonds for ethylene glycol?
+
+%  Ethylene glycol, a diol, has two hydrogen bond donor groups.
+%  \begin{itemize}
+%	\item Can hydrogen bond with same moeity.
+%	\item Can hydrogen bond with different moeities in the same 
+%	vicinity. 
+%	\item Dwell times tend to be shorter. If one hydroxyl group is bound
+%	with a hydrogen bond, the other unbound hydroxyl group may form a hydrogen bond
+%	elsewhere and effectively pull the other bound hydroxyl group along with it. 
+%  \end{itemize}
+
+  \subsection*{Sulfur Analogs}
+
+  We studied the transport properties of sulfur analogs of glycerol and ethylene glycol.
+  \begin{itemize}
+    \item We replaced all but one oxygen atom of each solute with sulfur atoms
+  	\item Sulfur is unable to hydrogen bond, however it is soluble in water  %BJC: maybe a reference to why sulfur can't hbond
+  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\linewidth}
+  \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
+  \caption{}\label{fig:SOH_GCL_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
+  \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
+  \caption{}\label{fig:DMP_GLY_comparison}
+  \end{subfigure}
+  \caption{}\label{fig:sulfur_analog_rdfs}
+  \end{figure}
+
+  \noindent Mercaptoethanol has a similar average RDF and MSD to ethylene glycol.
+  \begin{itemize}
+    \item There is a much larger uncertainty associated with mercaptoethanol's MSD
+    % BJC: hypothesis about observation. Remains to be quantified
+    \item Mercaptoethanol exhibits some of the largest single observed hops among all solutes.
+    \item Less frequent hydrogen bonding and an affinity for the pore region may be responsible
+    for these hops.
+  \end{itemize}
+
+  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
+  near monomer head groups. %BJC: should I give all the solutes nicknames (i.e. their residue names)?
+  \begin{itemize}
+    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
+    \item It can also hydrogen bond with water molecule
+    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups so it stays
+    close to pore walls.
+  \end{itemize}
+
+  Similar rdfs of ethylene glycol and dimercaptoethanol reinforces the lack of influence of hbonding % not really?
 
@@
   \end{itemize}
-
-  \subsection*{Transport of Acetic Acid}
 

### 2019-02-15 Ben_Manuscripts/transport/figures/avg_hbonds.py

@@ -6,44 +6,30 @@ from LLC_Membranes.llclib import file_rw, topology
 from LLC_Membranes.analysis.hbonds import System, Topology, Residue
 import names
 
-
-def calculate_moving_average(data, n):
-    """ Calculate moving average of a time series
-
-    :param n: Number of previous points to average
-
-    :type n: int
-    """
-
-    ret = np.cumsum(data, dtype=float)
-    ret[n:] = ret[n:] - ret[:-n]
-    return ret[n - 1:] / n
-
-
-def smooth(y, box_pts):
-    box = np.ones(box_pts) / box_pts
-    y_smooth = np.convolve(y, box, mode='same')
-    return y_smooth
-
+## Former avg_hbonds.py moved to hbonds.py ##
 
 path = "/home/bcoscia/Documents/Gromacs/Transport/NaGA3C11"
 #solutes = ["GLY", "GCL", "PG"]
 solutes = ["TET", "RIB"]
 solutes = ["GCL", "SOH", "GLY", "DMP"]
+solutes = ["MET", "ETH", "PR", "BUT", "GCL", "PG", "GLY", "TET", "RIB"]
+resnames = [names.res_to_name[i] for i in solutes]
 nsolutes = 24
 npts_ma = 8  # number of points to average over in moving average
 
+n = []
+n_std = []
+start = 0 
+
 for i in solutes:
     sys = file_rw.load_object('%s/%s/10wt/hbonds.pl' % (path, i))
-    n = [a.shape[1] / nsolutes for a in sys.hbonds]
-    #plt.plot(sys.t.time[:-(npts_ma - 1)] / 1000, calculate_moving_average(n, npts_ma))
-    #plt.plot(sys.t.time / 1000, n)
-    plt.plot(sys.t.time / 1000, smooth(n, npts_ma), label=names.res_to_name[i])
+    hbonds = [a.shape[1] / nsolutes for a in sys.hbonds]
+    n.append(np.mean(hbonds))
+    n_std.append(np.std(hbonds))
 
-#plt.ylim(0, 1)
-plt.xlabel('Time (ns)', fontsize=14)
-plt.ylabel('Number of hydrogen bonds per solute', fontsize=14)
+plt.bar(resnames, n) #, yerr=n_std) do error bars make sense for high fluctuations?
+plt.xticks(rotation=75)
+plt.ylabel('Average hydrogen bonds \n per solute', fontsize=14)
[…]

### 2019-02-15 Ben_Manuscripts/transport/figures/intramolecular_hbonds.py

@@ -1,0 +1,66 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+from LLC_Membranes.llclib import file_rw, topology
+from LLC_Membranes.analysis.hbonds import System, Topology, Residue
+import names
+
+path = "/home/bcoscia/Documents/Gromacs/Transport/NaGA3C11"
+solutes = ["GCL", "PG", "GLY", "TET", "RIB"]
+resnames = [names.res_to_name[i] for i in solutes]
+for i, n in enumerate(resnames):
+    if len(n.split()) == 2:
+        resnames[i] = n.split()[0] + '\n' + n.split()[1]
+nsolutes = 24
+
+n = []
+n_std = []
+start = 0
+
+fig, ax = plt.subplots(figsize=(10, 5))
+bar_width = 0.2
+opacity = 0.8
+loc = 0
+
+xticks = []
+for nd, i in enumerate(solutes):
+    n = 0
+
+    sys = file_rw.load_object('%s/%s/10wt/hbonds.pl' % (path, i))
+    res_numbers = sys.number_residues(i)[0]  # dictionary for converting index to residue number (residue 0 through residue 23)
+
+    for a in sys.hbonds:
+       for ndx, k in enumerate(a[0]):
+           donor = res_numbers[k]
+           try:
+               acceptor = res_numbers[a[2][ndx]]
+               if acceptor == donor:
+                   n += 1
+           except KeyError:
+               pass
+#        donors = np.array([res_numbers[int(j)] for j in a[0]], dtype=int)
+#        acceptors = np.array([res_numbers[int(j)] for j in a[2]], dtype=int)
+#        intra = (donors == acceptors)  # find cases where a donor and acceptor are on the same solute
+
+    ax.bar(resnames[nd], n, bar_width)
+
+#from matplotlib.patches import Patch 
+#custom = [Line2D([0], [0], color='xkcd:blue', lw=4, alpha=opacity),
+#          Line2D([0], [0], color='xkcd:orange', lw=4, alpha=opacity),
+#          Line2D([0], [0], color='xkcd:green', lw=4, alpha=opacity),
+#          Line2D([0], [0], color='xkcd:red', lw=4, alpha=opacity)]
+#custom = [Patch(facecolor='xkcd:blue', alpha=opacity),
[…]

### 2019-02-15 analysis/solute_order.py

@@ -194,7 +194,6 @@ class System(object):
                 ndx = np.where(~self.solute_partition[i, ])[0]
             else:
                 ndx = np.arange(self.costheta.shape[1])
-            print(len(ndx))
             # 2D (https://physics.stackexchange.com/questions/65358/2-d-orientational-order-parameter)
             self.nematic_order_parameter[i] = np.sum(2 * self.costheta[i, ndx] ** 2 - 1) / len(ndx)
 

### 2019-02-15 Ben_Manuscripts/transport/Outline.tex
Added outline

@@
 
-  \subsection*{Sulfur Analogs}
+  \subsection*{Transport of Thiols} % BJC: maybe put this after next section and call it sulfur analogs and include DMSO?
 
@@
     \item Glycerol frequently hydrogen bonds with more than one head group at a time.
-    \item It can also hydrogen bond with water molecule
+    \item It also hydrogen bond with water molecules which causes it to stay in the pore region
     \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups so it stays
@@
 
-  Similar rdfs of ethylene glycol and dimercaptoethanol reinforces the lack of influence of hbonding % not really?
+  \subsection*{Transport of Ketones}
 
-  \subsection*{Transport of Ketone-like Solutes}
+  %BJC: DMSO might be added to this section. 
+  %BJC: DMSO might be slow because it's miscible in organic and polar solvents
 
-  The carbonyl group of Acetone is a hydrogen bond acceptor and therefore only
-  form hydrogen bonds with water molecules in the pore.
-
-  The hydrophobic character of the two methyl groups on acetone causes the methyl
-  groups to gravitate towards the outside of the pore, while the carbonyl group
-  reaches towards the pore center in order to hydrogen bond with water molecules.
+  The 4 ketone-like molecules tested show a range of transport behaviors.
   \begin{itemize}
-	\item Order parameter defined between vector along carbonyl and vector extending
-	from acetone COM to pore center is non-zero.
+    \item Urea, Acetic Acid, Acetamide and Acetone are all characterized by a carbonyl group
+    with two attached heavy atoms. 
+    \item All have approximately the same molecular weight and are planar molecules due to
+    the sp2 hybridization of the carbonyl group.
+    \item The fastest solute of this grouping, Urea, has an MSD comparable to that of ethylene
+    glycol while the slowest, Acetone, has an MSD one third of that of Urea.
   \end{itemize}
 
-  Acetic acid, since we modeled it solely in its protonated state, has hydrogen
-  bond donor and acceptor groups.
-
-  \subsection*{Transport of Ions} % probably just sodium
-
-  Sodium ions also exhibit hop diffusion because polarized water and
-  carboxylate head groups both work to neutralize its charge.
+  Once again, the trends in the MSD can in large part be explained by the solutes'
+  ability to hydrogen bond.  % or maybe just polarity
   \begin{itemize}
-	\item Ions get trapped in oxygen 'cages' composed of combinations
-	of water molecules, carboxylate head groups and ether oxygens connecting
-	the head groups to their tails.
-  	\item Interesting coordination number data
-	\item Dwell time proportional to surrounding charge within coordination shell
+  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
+  	while acetone is the first instance of a molecule in this study that can only
+  	accept hydrogen bonds.
+  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
+  	its density is high near the pore center, particularly near the monomer head groups.
+  	\item Acetamide has only one nitrogen atom. One of two peaks in its density is 
+  	located close to the peak of Urea, likely corresponding to hydrogen bonds with head groups.
+  	A second peak is located within the head group region. %BJC: hbonds with ethers vs. head groups. Or is it just planarity?
+  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
+  	a peak close to the carboxylate groups.  %BJC: hbonds with 
+  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
+    its low polarity and planar shape gives it comparable stability when trapped between head groups.
+%  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
+%  	other is relatively deep in the head group region.
   \end{itemize}
 
-  \subsubsection*{Remarks}
+  \subsection*{Hydrogen bond acceptors}  % Need a better heading since all molecules in this study are acceptors
 
-  Overwhelming amount of water in 10 wt\% system makes hydrogen bonding
-  competitive between head groups and water.
-  %MRS: not sure what you mean above.
+  The final set of molecules we studied can accept hydrogen bonds, but cannot donate
+  them. 
+  \begin{itemize}
+  	\item Among this set are the two slowest solutes in our study: Tetrahydrofuran and Dimethyl Formamide.
+  	\item Ethyl acetate and Propylene Carbonate are only marginally faster, however they
+  	are both larger molecules. %BJC: not sure how far I should dive into this point
+  \end{itemize}
 
-  \subsection{Design Suggestions}
+  The radial density functions highlight the solutes' preference for the 
+  pore region.
+  \begin{itemize}
+  	\item There are small peaks in the radial density greater than 1 nm 
+  	from the pore center.
+  	\item The solutes become trapped in these regions where each step is
+  	highly anti-correlated to its previous step, leading to very low MSDs.
+  	\item The large size and nonplanar shapes of ethyl acetate and propylene 
+  	carbonate may destabilize entrapment in the tail region more quickly, leading
+  	to slightly faster transport. 
+%  	\item The relatively small amount of movement on the timescales studied 
+%  	do not reveal definitive reasons
+  	\item Overall, 
+  \end{itemize}
+  Ethyl acetate spends all of its time in a linear or near-linear conformation. % can show with dihedrals
+
+  THF and DMF are both planar which allows them to
+
+  % THF shows highly anticorrelated hops
+
+  %All have comparable densities near pore center except acetone which is lower
+
+%  \subsection*{Transport of Ions} % probably just sodium
+%
+%  Sodium ions also exhibit hop diffusion because polarized water and
+%  carboxylate head groups both work to neutralize its charge.
+%  \begin{itemize}
+%	\item Ions get trapped in oxygen 'cages' composed of combinations
+%	of water molecules, carboxylate head groups and ether oxygens connecting
+%	the head groups to their tails.
+%  	\item Interesting coordination number data
+%	\item Dwell time proportional to surrounding charge within coordination shell
+%  \end{itemize}
+
+  \subsection{Design Principles}
 

### 2019-02-15 Ben_Manuscripts/transport/figures/same_residue_rdf.py

@@ -6,8 +6,8 @@ from LLC_Membranes.llclib import file_rw
 import matplotlib.pyplot as plt
 import names
 
-r = 'DMP'
-atoms = ['O', 'S', 'S1']
+r = 'EAC'
+atoms = ['C', 'C3']
 wt=10
 maximum = 0
 

### 2019-02-15 llclib/physical.py

@@ -657,7 +657,7 @@ def partition(com, pore_centers, r, buffer=0, unitcell=None, npores=4, spline=Fa
     :type spline: bool
 
     :return part: boolean numpy array with shape (nT, com.shape[1]) where True indicates a center of mass that is
-    inside the pore region
+    inside the inner region (i.e. < r)
     """
 
     nT = com.shape[0]

### 2019-02-19 Ben_Manuscripts/transport/Outline.tex
More figures

@@
   	uncertainty at k=1, the most insightful data point. This behavior is consistent across
-  	all solutes molecules.
+  	all solutes molecules. % Can put error bars on points
   	\item Therefore, we believe transport can be described as subordinated fractional Brownian
@@
   	with one of the five oxygen atoms attached to each monomer head group. 
-  	\item In a separate interaction, solutes can become kinetically trapped between 
+  	\item In a separate interaction, solutes can become kinetically trapped between or behind
   	monomer head groups. These interactions likely lead to the observed anti-correlated
@@
     solubility.
-    \item Small, planar molecules like acetone exhibit some of the slowest MSDs.
-    Their flat geometry and small size makes it easy for them to get lodged deep
-    between head groups.
+    \item Small, planar molecules, without the ability to donate hydrogen bonds, like acetone,
+    exhibit some of the slowest MSDs. Their flat geometry and small size makes it easy for 
+    them to get lodged deep between head groups.
   	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
@@
   \end{itemize}
+
+  %BJC: potential figure to go with above paragraph
+  % (a) Plot showing how biggest jumps are at pore center
+  % (b) Illustrate preference for hbonds carboxylate head groups
 
@@
   \begin{itemize}  
-    \item The radial distribution as a function of distance from the pore center
+    \item The radial density as a function of distance from the pore center
     for each alcohol is plotted in Figure~\ref{fig:simple_alcohol_rdf}.
@@
     less than the density near the head groups.
-    \item All other alcohol molecules are concentrated in the head group region.
+    \item All other alcohol molecules are most concentrated in the head group region.
   \end{itemize}
@@
   \begin{itemize}
-    \item Extra hydroxyl groups cause solutes to favor the water-rich pore region
+    \item Extra hydroxyl groups cause solutes to favor the water-rich pore region.
     where there is the least hindrance to movement.
     \item However, these extra hydroxyl groups facilitate a larger number of 
-    hydrogen bond interactions that work to hold solutes in place.
+    hydrogen bond interactions that work to hold solutes in place (See Figure~\ref{fig:multi_hbonds}).
     \item At the same time, solute molecular weight increases, which inherently
@@
     head groups simultaneously.
-%  	\item Simple alcohols, containing only one hydroxyl group, hydrogen bond
-%  	with head groups about 20 \% of the time. % BJC: I have a figure showing the average number of hydrogen bonds per solute
   \end{itemize}
@@
   	relatively fast MSD. 
+  	%BJC: number of PG vs ethylene glycol that enters middle -- I don't think this will be any different than density function
     \item Both diols have comparable densities close to the pore center, however propylene glycol's
@@
     \item Combined with an increase in molecular weight, the addition of a single methyl group
-    increases the molecule's hydophobic character and causes propylene glycol to favor positions
+    increases the molecule's hydrophobic character and causes propylene glycol to favor positions
     near monomer head groups.
@@
     carboxylate groups, explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
-    % BJC: could plot dwell time as a function of radial position (show that dwells are longest when PG
-    % is hbonding to head groups
   \end{itemize}
+
+  % BJC: figure does not represent total number of hops (PG has less hops)
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=\linewidth]{dwell_hop_PG_GCL.pdf}
+  \caption{}\label{fig:dwell_hop_PG_GCL}
+  \end{figure}
 
@@
   	\item Their large size and high hydrogen bonding capability prevents them
-  	from have larger MSDs.
+  	from having larger MSDs.
   \end{itemize}
@@
 
-  \subsection*{Transport of Thiols} % BJC: maybe put this after next section and call it sulfur analogs and include DMSO?
-
-  We studied the transport properties of sulfur analogs of glycerol and ethylene glycol.
-  \begin{itemize}
-    \item We replaced all but one oxygen atom of each solute with sulfur atoms
-  	\item Sulfur is unable to hydrogen bond, however it is soluble in water  %BJC: maybe a reference to why sulfur can't hbond
-  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
-  \end{itemize}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\linewidth}
-  \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
-  \caption{}\label{fig:SOH_GCL_comparison}
-  \end{subfigure}
-  \begin{subfigure}{0.45\linewidth}
-  \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
-  \caption{}\label{fig:DMP_GLY_comparison}
-  \end{subfigure}
-  \caption{}\label{fig:sulfur_analog_rdfs}
-  \end{figure}
-
-  \noindent Mercaptoethanol has a similar average RDF and MSD to ethylene glycol.
-  \begin{itemize}
-    \item There is a much larger uncertainty associated with mercaptoethanol's MSD
-    % BJC: hypothesis about observation. Remains to be quantified
-    \item Mercaptoethanol exhibits some of the largest single observed hops among all solutes.
-    \item Less frequent hydrogen bonding and an affinity for the pore region may be responsible
-    for these hops.
-  \end{itemize}
-
-  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
-  near monomer head groups. %BJC: should I give all the solutes nicknames (i.e. their residue names)?
-  \begin{itemize}
-    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
-    \item It also hydrogen bond with water molecules which causes it to stay in the pore region
-    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups so it stays
-    close to pore walls.
-  \end{itemize}
-
   \subsection*{Transport of Ketones}
-
-  %BJC: DMSO might be added to this section. 
-  %BJC: DMSO might be slow because it's miscible in organic and polar solvents
 
@@
 
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.45\textwidth]{ketone_rdf.pdf}
+  \caption{}\label{fig:ketones_rdf}
+  \end{figure}
+
+  \subsection*{Transport of Thiols}
+
+  We studied the transport properties of sulfur analogs of glycerol, ethylene glycol 
+  and acetone.
+%  Finally, we studied the transport properties of sulfur-containing compounds similar
+%  to some of the solutes studied above.
+  \begin{itemize}
+    \item We replaced all but one oxygen atom of ethylene glycol and glycerol with sulfur atoms
+    to create Dimercaptoethanol and 2,3-Dimercapto-1-propanol.
+    \item We replaced the carbonyl carbon of acetone with sulfur in order to create DMSO. 
+  	\item Sulfur is unable to hydrogen bond, however it is soluble in water  %BJC: maybe a reference to why sulfur can't hbond
+  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.325\linewidth}
+  \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
+  \caption{}\label{fig:SOH_GCL_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.325\linewidth}
+  \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
+  \caption{}\label{fig:DMP_GLY_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.325\linewidth}
+  \includegraphics[width=\textwidth]{thiol_comparison_DMS.pdf}
+  \caption{}\label{fig:DMP_GLY_comparison}
+  \end{subfigure}
+  \caption{}\label{fig:sulfur_analog_rdfs}
+  \end{figure}
+
+  \noindent Mercaptoethanol has a similar average RDF and MSD to ethylene glycol.
+  \begin{itemize}
+    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
+    \item It spends more time in the tail region than ethylene glycol, where transport
+    is inherently slower, and may contribute to some slower MSDs.  % Can quantify as a percentage
+    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs % BJC: hypothesis about observation. Remains to be quantified
+    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
+    % Dwell time as a function of hbonds?
+    \item Some of this can be accounted for by the higher density of mercaptoethanol 
+    molecules in the head group / tail region.
+    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
+    monomer head group simultaneously,
+
+    \item Less frequent hydrogen bonding and an affinity for the pore region may be
+    responsible for these hops.
+  \end{itemize}
+
+  % Potentially useful explanation
+%  Ethylene glycol has a high chance of hydrogen bonding at least once with monomer head groups. 
+%  An ethylene glycol molecule can hydrogen bond twice simultaneously.
+%  When one of those hydrogen bond breaks, the molecule is still stabilized by another hydrogen bond
+%  It can easily reform the second hydrogen bond in close proximity
+
+  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
+  near monomer head groups. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
+  \begin{itemize}
+    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
+    % BJC: can probably quantify the following:
+    \item It also hydrogen bonds with water molecules which increases its stability in the pore region
+    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups so it gravitates
+    towards the head group region.
+  \end{itemize}
+
+  \noindent DMSO has a comparable MSD to acetone even though its molecular weight is
+  about 25 \% larger.
+  \begin{itemize}
+  	\item The pyramidal structure of DMSO may force it to spend more time closer to
+  	the pore center.  % BJC: might be a good place for a numbers comparison
+  	\item There are 20 \% more acetone than DMSO molecules in the region beyond 0.8 nm from the pore center.  % based on actual number, not density
+  	\item DMSO cannot as easily work its way in and out of the dense head group region. 
+  	\item There is a peak in DMSO's radial density near 1.1 nm which may be a consequence of 
+  	solute molecules that get stuck in the tails.
+%    \item This may be due to the higher polarity and the pyramidal structure of DMSO.
+%    \item DMSO is more stable in water than acetone and less stable in the head group region than acetone.
+%    \item There is a peak in the DMSO radial density function in the tails which means some of them still
+%    find their way back there and get trapped.
+  \end{itemize}
+
   \subsection*{Hydrogen bond acceptors}  % Need a better heading since all molecules in this study are acceptors
@@
   	to slightly faster transport. 
+  	% BJC:  Ethyl acetate spends all of its time in a linear or near-linear conformation.
 %  	\item The relatively small amount of movement on the timescales studied 
@@
   \end{itemize}
-  Ethyl acetate spends all of its time in a linear or near-linear conformation. % can show with dihedrals
 
-  THF and DMF are both planar which allows them to
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{nondonors_rdf.pdf}
+  \caption{}\label{fig:nondonors_rdf}
+  \end{figure}
 

### 2019-02-19 analysis/msd.py

@@ -152,16 +152,16 @@ class Diffusivity(object):
 
         # plot 'random' z coordinate traces
         # np.random.seed(4)  # 4 gives a nice spread for ethanol
-        # trajs = np.random.randint(0, self.com.shape[1], size=3)
+        # trajs = np.random.randint(0, self.com.shape[1], size=24)
         # for i in trajs:
         #     plt.plot(self.time, self.com[:, i, 2], linewidth=2)
         #
-        # plt.ylabel('$z$-coordinate (nm)', fontsize=14)
-        # plt.xlabel('Time (ns)', fontsize=14)
-        # plt.gcf().get_axes()[0].tick_params(labelsize=14)
-        # plt.tight_layout()
+        #     plt.ylabel('$z$-coordinate (nm)', fontsize=14)
+        #     plt.xlabel('Time (ns)', fontsize=14)
+        #     plt.gcf().get_axes()[0].tick_params(labelsize=14)
+        #     plt.tight_layout()
         #
-        # plt.show()
+        #     plt.show()
         # exit()
 
         self.weights = True
@@ -218,11 +218,15 @@ class Diffusivity(object):
 
         print('Calculating MSD...', end='', flush=True)
         self.MSD = timeseries.msd(self.com, self.axis, ensemble=ensemble)
-        # for i in range(self.MSD.shape[1]):
-        #     print(np.amax(self.MSD[:, i]), i)
-        #     #plt.plot(self.MSD[:, i])
-        # #plt.show()
-        # exit()
+        highest = np.argmax(self.MSD[-1, :])
+        plt.plot(self.time, self.com[:, highest, 2], linewidth = 2)
+        # plt.plot(self.MSD[:, highest])
+        plt.show()
+        exit()
+        for i in range(self.MSD.shape[1]):
+            plt.plot(self.MSD[:, i])
+        plt.show()
+        exit()
         self.MSD_average = np.mean(self.MSD, axis=1)
         print('Done!')
 

### 2019-02-20 Ben_Manuscripts/transport/Outline.tex
Updates to outline

@@
 
-  The 4 ketone-like molecules tested show a range of transport behaviors.
+  The 4 ketone-like molecules tested show a surprising range of transport behaviors.
   \begin{itemize}
@@
     the sp2 hybridization of the carbonyl group.
-    \item The fastest solute of this grouping, Urea, has an MSD comparable to that of ethylene
-    glycol while the slowest, Acetone, has an MSD one third of that of Urea.
+    \item The fastest solute of this grouping, Urea (comparable to Acetic Acid too), has an
+    MSD comparable to that of ethylene glycol while the slowest, Acetone, has an MSD one 
+    third of that of Urea.
   \end{itemize}
@@
   Once again, the trends in the MSD can in large part be explained by the solutes'
-  ability to hydrogen bond.  % or maybe just polarity
+  preference for water.
   \begin{itemize}
@@
   	while acetone is the first instance of a molecule in this study that can only
-  	accept hydrogen bonds.
+  	accept hydrogen bonds. It follows that acetone has the slowest MSD of this grouping.
+  	\item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
+  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
+  	\item Hence, Acetic Acid donates the greatest number of hydrogen bonds and has
+  	the highest density throughout the pore region.
+  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
+  	expect Urea to exhibit much faster transport, however its MSD is comparable to
+  	the much stickier acetic acid. 
+  	\item Urea is highly soluble in water but not miscible in all proportions like 
+  	acetic acid or even acetone.
+  	\item Relative to acetic acid, acetamide, urea and acetone spend more time in the head group region.
+  	\item There is a large peak near the head groups, but \% of the urea molecules 
+  	are behind in the head group region.
+  	\item The structure of acetamide differs from acetic acid only by an amine group in place
+  	of a hydroxyl group.
+  	\item The weaker hydrogen bonding capability of acetamide and an extra nonpolar methyl group compared to
+  	Urea makes acetamide even more likely to partition. 
   	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
   	its density is high near the pore center, particularly near the monomer head groups.
+
   	\item Acetamide has only one nitrogen atom. One of two peaks in its density is 
@@
   	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
-  	a peak close to the carboxylate groups.  %BJC: hbonds with 
+  	a peak close to the carboxylate groups.  %BJC: hbonds a lot 
   	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{ketone_rdf.pdf}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ketone_rdf.pdf}
   \caption{}\label{fig:ketones_rdf}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ketone_ratio.pdf}
+  \caption{}\label{fig:ketones_ratio}
+  \end{subfigure}
   \end{figure}
@@
     \item Some of this can be accounted for by the higher density of mercaptoethanol 
-    molecules in the head group / tail region.
+    molecules in the head group / tail region. There are nearly 40 \% more mercaptoethanol
+    beyond 0.8 nm from the pore center. 
     \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
@@
   \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{SOH_trace.pdf}
+  \caption{}\label{fig:SOH_trace}
+  \end{subfigure}
+  \caption{}
+  \end{figure}
 
@@
   The radial density functions highlight the solutes' preference for the 
-  pore region.
+  head group region.
   \begin{itemize}

### 2019-02-20 Ben_Manuscripts/transport/figures/traces.py

@@ -1,0 +1,15 @@
+#!/usr/bin/env python
+
+from LLC_Membranes.analysis.ztrace import ZTrace
+from LLC_Membranes.llclib import file_rw
+import matplotlib.pyplot as plt
+
+residue = "SOH"
+indices = [17, 3]  # residue number whose z trace to plot
+wt = 10
+
+path = "/home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/%s/%swt/trace.pl" % (residue, wt)
+
+trace = file_rw.load_object(path)
+
+trace.plot_trace(indices, cmax=1.5, savename="%s_trace.pdf" % residue)

### 2019-02-21 Ben_Manuscripts/transport/Outline.tex
Updates to outline

@@
 
-  Water molecules also exhibit hop diffusion.
-
-  The overwhelming number of water molecules reduces
-
-  Even in the center of the pore, where the density of water molecules is
-  highest, individual water molecules exhibit hop diffusion as they create a
-  tight hydrogen bond network.
-  %TODO: the following is a hypothesis
+  The MSD of water is a weak function of the solute residue disolved in
+  the pores.
   \begin{itemize}
-	\item Water sticks to pore walls
-	\item Dwell times are short
-	\item Water tumbles across pore for a while until it sticks again. 
-	\item Water gets caught in h-bonds with other water molecules away
-	from pore center.
+  	\item Large molecules like glycerol and ribose obstruct the movement
+  	of water molecules forcing them to have lower MSDs
+  	\item I don't know why the MSD is fast in the fastest systems or why DMSO is slow.
+  	\item Sulfur containing compounds have slowest water transport
+  	\item How do 24 solute molecules have such a drastic effect on water motion
   \end{itemize}
 
-  In this confined environment, the diffusion constant is x times lower than
-  expected bulk diffusion coefficient of tip3p water.
+  % BJC: MSDs only calculated for water molecules that spend > 95 % of their
+  % time in the pore. Pore region / tail region cutoff is at 1.5 nm (approximate location of lowest radial water density) 
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{water_msd.pdf}
+  \caption{}\label{fig:water_msd}
+  \end{figure}
 
-  %TODO: study diffusion mechanism of water
+  % BJC. Other Notes:
+  % There is no discernable trend in flux of water to/from pores. Most levels stay 
+  % comparable to their initial values while a handful have ~50 water molecules that
+  % enter the pore during the simulation.
+  % Water molecules that spend > 95 % of their time within 1 nm of the pore center 
+  % have lower MSDs -- although there aren't a lot of them to average over. They are
+  % probably lower because they can't be moving much to stay so confined
 
@@
   	the highest density throughout the pore region.
-  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
-  	expect Urea to exhibit much faster transport, however its MSD is comparable to
-  	the much stickier acetic acid. 
-  	\item Urea is highly soluble in water but not miscible in all proportions like 
-  	acetic acid or even acetone.
-  	\item Relative to acetic acid, acetamide, urea and acetone spend more time in the head group region.
-  	\item There is a large peak near the head groups, but \% of the urea molecules 
-  	are behind in the head group region.
-  	\item The structure of acetamide differs from acetic acid only by an amine group in place
-  	of a hydroxyl group.
-  	\item The weaker hydrogen bonding capability of acetamide and an extra nonpolar methyl group compared to
-  	Urea makes acetamide even more likely to partition. 
-  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
-  	its density is high near the pore center, particularly near the monomer head groups.
-
-  	\item Acetamide has only one nitrogen atom. One of two peaks in its density is 
-  	located close to the peak of Urea, likely corresponding to hydrogen bonds with head groups.
-  	A second peak is located within the head group region. %BJC: hbonds with ethers vs. head groups. Or is it just planarity?
-  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
-  	a peak close to the carboxylate groups.  %BJC: hbonds a lot 
-  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
-    its low polarity and planar shape gives it comparable stability when trapped between head groups.
+  	\item All other solutes show a higher preference for the tail region where three 
+  	dimensional confinement directly contributes to a lower MSD.
+  	\item Urea likely compensates for its loss of mobility in the head group region by
+  	making large hops upon escape into the pore region.
+  	\item Urea frequently moves between the head group and pore region because its planar
+  	shape makes it easier to transition between regions.% could quantify transition frequency probably. It seems like it might yield something. But also might make things more ambiguous.
+  	\item As the solutes become less polar, their MSD decreases. 
+  	\item Acetamide has one less amine group than Urea and a corresponding smaller MSD.
+  	\item Despite a peak in its density near the pore center due to its water solubility,
+  	Acetone is the least polar and spends the most time outside the tail group region 
+  	leading to the lowest MSD.
+%  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
+%  	expect Urea to exhibit much faster transport, however its MSD is comparable to
+%  	the much stickier acetic acid. 
+%  	\item Urea is highly soluble in water but not miscible in all proportions like 
+%  	acetic acid or even acetone.
+%  	\item Relative to acetic acid, acetamide, urea and acetone spend more time in the head group region.
+%  	\item There is a large peak near the head groups, but \% of the urea molecules 
+%  	are behind in the head group region.
+%  	\item The structure of acetamide differs from acetic acid only by an amine group in place
+%  	of a hydroxyl group.
+%  	\item The weaker hydrogen bonding capability of acetamide and an extra nonpolar methyl group compared to
+%  	Urea makes acetamide even more likely to partition. 
+%  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
+%  	its density is high near the pore center, particularly near the monomer head groups.
+%  	
+%  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
+%  	a peak close to the carboxylate groups.  %BJC: hbonds a lot 
+%  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
+%    its low polarity and planar shape gives it comparable stability when trapped between head groups.
 %  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
@@
 
-  We studied the transport properties of sulfur analogs of glycerol, ethylene glycol 
-  and acetone.
+  We also studied the transport properties of sulfur analogs of glycerol, ethylene
+  glycol and acetone.
 %  Finally, we studied the transport properties of sulfur-containing compounds similar
@@
     is inherently slower, and may contribute to some slower MSDs.  % Can quantify as a percentage
-    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs % BJC: hypothesis about observation. Remains to be quantified
+    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs  % Only methanol has greater (I think)
     \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
-    % Dwell time as a function of hbonds?
+    \item This may lead to larger hops in the pore region.
     \item Some of this can be accounted for by the higher density of mercaptoethanol 
     molecules in the head group / tail region. There are nearly 40 \% more mercaptoethanol
-    beyond 0.8 nm from the pore center. 
-    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
-    monomer head group simultaneously,
-
-    \item Less frequent hydrogen bonding and an affinity for the pore region may be
-    responsible for these hops.
+    molecules than ethylene glycol molecules beyond 0.8 nm from the pore center. 
+%    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
+%    monomer head group simultaneously,
+%    \item Less frequent hydrogen bonding and an affinity for the pore region may be
+%    responsible for these hops.
   \end{itemize}
@@
     % BJC: can probably quantify the following:
-    \item It also hydrogen bonds with water molecules which increases its stability in the pore region
-    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups so it gravitates
-    towards the head group region.
+    \item It also hydrogen bonds with water molecules which increases its stability
+    in the pore region.
+    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups 
+    so it gravitates towards the head group region.
   \end{itemize}
@@
   	the pore center.  % BJC: might be a good place for a numbers comparison
-  	\item There are 20 \% more acetone than DMSO molecules in the region beyond 0.8 nm from the pore center.  % based on actual number, not density
-  	\item DMSO cannot as easily work its way in and out of the dense head group region. 
+  	\item There are 20 \% more acetone than DMSO molecules in the region beyond 
+  	0.8 nm from the pore center.  % based on actual number, not density
+  	\item DMSO cannot as easily work its way in and out of the dense head group region. % BJC: some kind of average regional lifetime
   	\item There is a peak in DMSO's radial density near 1.1 nm which may be a consequence of 
   	solute molecules that get stuck in the tails.
-%    \item This may be due to the higher polarity and the pyramidal structure of DMSO.
-%    \item DMSO is more stable in water than acetone and less stable in the head group region than acetone.
-%    \item There is a peak in the DMSO radial density function in the tails which means some of them still
-%    find their way back there and get trapped.
   \end{itemize}
@@
 
-%  \subsection*{Transport of Ions} % probably just sodium
-%
+  \subsection*{Transport of Ions} % probably just sodium
+
+  Sodium ions coordinate with water molecules.
+
 %  Sodium ions also exhibit hop diffusion because polarized water and
@@
 
-  Water content affects pore size. Experiments to understand this could be useful.
+  Water content affects pore size and strongly influence the MSD of both solutes and
+  water. Experiments to understand how controllable this parameter is could be useful.
 
-  Separate polar molecules by creating monomers with more hydrophilic head group components.
-  More incentive to dwell on walls.
+  Monomers that cannot hydrogen bond. % Hard to make a monomer like this
 
-  Make ions move faster by placing charges in sterically inaccessible places.
+  Separate polar molecules by creating monomers with head group components designed to
+  hydrogen bond.
+  \begin{itemize}
+  	\item Hbond donors
+	\item More incentive to dwell on walls.
+  \end{itemize}
 
@@
 	over polar molecules
-	\item Also separate acetone (things with only h-bond accepting groups) in this way
   \end{itemize}

### 2019-02-21 analysis/msd.py

@@ -39,7 +39,10 @@ def initialize():
     parser.add_argument('-acf', '--autocorrelation', action="store_true", help='Plot step autocorrelation function')
     parser.add_argument('-acov', '--autocovariance', action="store_true", help='Plot step autocovariance function')
     parser.add_argument('-nofit', '--nofit', action="store_true", help='Do not attempt to fit any curve to MSD')
+
     parser.add_argument('--update', action="store_true", help="update database with MD MSD values")
+    parser.add_argument('-wt', '--wt_water', default=10, type=float, help='Weight percent water in system. Only need'
+                                                                          'to adjust this if updating database.')
 
     return parser
 
@@ -75,6 +78,7 @@ class Diffusivity(object):
         print('Done!')
         self.nT = self.t.n_frames  # number of frames
         self.time = self.t.time / 1000  # time stamp on each frame, converted to nanoseconds
+        print(self.time[-1])
 
         # initialize fits to data, error analysis and plotting parameters
         self.startfit = int(startfit*self.nT)  # index at which to start fit
@@ -193,7 +197,7 @@ class Diffusivity(object):
         pore_atoms = [a.index for a in self.t.topology.atoms if a.name in pore_defining_atoms]
         if spline:
             print('Creating pore splines')
-            pore_centers = physical.trace_pores(self.t.xyz[:, pore_atoms, :], self.t.unitcell_vectors, 20)
+            pore_centers = physical.trace_pores(self.t.xyz[:, pore_atoms, :], self.t.unitcell_vectors, 10)
         else:
             pore_centers = physical.avg_pore_loc(npores, self.t.xyz[:, pore_atoms, :], self.t.unitcell_vectors)
 
@@ -218,15 +222,15 @@ class Diffusivity(object):
 
         print('Calculating MSD...', end='', flush=True)
         self.MSD = timeseries.msd(self.com, self.axis, ensemble=ensemble)
-        highest = np.argmax(self.MSD[-1, :])
-        plt.plot(self.time, self.com[:, highest, 2], linewidth = 2)
-        # plt.plot(self.MSD[:, highest])
-        plt.show()
-        exit()
-        for i in range(self.MSD.shape[1]):
-            plt.plot(self.MSD[:, i])
-        plt.show()
-        exit()
+        # highest = np.argmax(self.MSD[-1, :])
+        # plt.plot(self.time, self.com[:, highest, 2], linewidth = 2)
+        # # plt.plot(self.MSD[:, highest])
[…]

### 2019-02-22 Ben_Manuscripts/transport/Outline.tex
Outline updoots

@@
 
-  In this work, we have determined the transport mechanisms and macroscopic
-  transport properties exhibited by a number of polar solutes with varying size,
-  chemical functionality and hydrophilic character.
+  In this work, we have studied the transport mechanisms exhibited by a number
+  of polar solutes with varying size, chemical functionality and hydrophilic character.
   \begin{itemize}
@@
 
-  We have compared our calculated diffusion coefficients with experimental
-  measurements made using DOSY NMR.
+  There are a number of questions that we wish to answer in order to create a
+  framework for studying this system in even greater detail.
+  \begin{enumerate}
+
+   	\item What transport mechanisms do we observe?
+
+  	Given that the pores will restrict motion of the solutes, we anticipate that 
+  	transport will be hindered in some way. We want to understand the differences in
+  	solute motion, specifically its mean squared displacement (MSD), based on a solute's
+  	size and chemical identity (functional groups). We will study the interactions
+  	between solutes, the membrane, and water in order to determine which mechanism
+  	or mechanisms dominate.
+
+%  	are dictated by a 
+%  	solute's chemical identity and if so, what interactions lead to this
+%  	difference.
+
+  	\item How do molecules, including water, partition within the pores?
+
+  	From a macroscopic perspective, it is straightforward to hypothesize that the water and
+  	polar solutes spend their time exclusively in the tube-like hydrophilic pore region.
+  	Our previous work showed that there is a gradual compositional transition from the 
+  	hydrophilic to the hydrophobic region which means that solutes may not 
+  	necessarily stay confined to the centers of the pores or even within the
+  	pore region. We will study the gradient in composition of solutes and water
+  	and any resultant influence it might have on mechanistic properties.
+
+  	\item Can we describe the transport mechanisms using pre-existing 
+  	mathematical models.
+
+  	A mathematical model may provide additional insight into the transport
+  	mechanisms and, in future work, can help relate performance on the 
+  	timescales studied with MD to macroscopic timescales. We will use
+  	qualitative and semi-quantitative arguments in order to choose a 
+  	governing model.
+
+  	\item How can we modify the current monomers in order to enhance
+  	solute-specific separations?
+
+  	Most experimental characterization up to this point has been centered 
+  	around the monomer, Na-GA3C11, studied here. The primary reason for conducting
+  	these simulations is to understand what chemical modifications can be made 
+  	to this or similar liquid crystal molecules in order to enhance transport 
+  	of desired species or restrict that of undesired species. We will use the 
+  	insight gained from our mechanistic observations in order to suggest new 
+  	monomer designs.
+
+  \end{enumerate}
+
+  There are number of questions this study is not intended to answer.
+  \begin{itemize}
+    \item We will not study the concentration dependence of the observed
+    transport rates. Although the average MSD might change with concentration,
+    we are focused on the underlying interactions leading to the observed 
+    transport mechanisms which we conjecture will be the same regardless of
+    concentration.
+    \item We will not study the chemical potential of solutes in the pores, which
+    could give us a better understanding of equilibrium solute partitioning.
+    However, this information will not greatly enhance our understanding of 
+    mechanistic details in various membrane regions.
+    \item Both of the above points will add unnecessary levels of complexity
+    which can be left for a future study. 
+%    \item Our work is meant as a simple starting point for studying transport
+%    mechanisms in these complex LLC systems.
+    \item This work is a simple starting point meant for observing the types
+    of interactions which occur between isolated solutes and the membrane.
+  \end{itemize}
 
@@
   \subsection*{Governing Mechanisms}\label{section:mechanism_overview}
+
+  We will answer the questions posed in the introduction in a general 
+  sense before addressing them with respect to specific molecules.
 
@@
 
-  \subsection*{Transport of Ketones}
+  \subsection*{Transport of Ketones and Amides}
 

### 2019-02-26 Ben_Manuscripts/transport/Outline.tex
Fixed imports and updated outlin

@@
 
-  There are a number of questions that we wish to answer in order to create a
-  framework for studying this system in even greater detail.
+%  There are a number of questions that we wish to answer in order to create a
+%  framework for studying this system in even greater detail.
+  There are a number of questions we wish to address in order to characterize
+  transport in this system.
   \begin{enumerate}
@@
   	solute motion, specifically its mean squared displacement (MSD), based on a solute's
-  	size and chemical identity (functional groups). We will study the interactions
+  	size, shape and chemical functionality. We will study the interactions
   	between solutes, the membrane, and water in order to determine which mechanism
   	or mechanisms dominate.
-
-%  	are dictated by a 
-%  	solute's chemical identity and if so, what interactions lead to this
-%  	difference.
 
@@
     transport rates. Although the average MSD might change with concentration,
-    we are focused on the underlying interactions leading to the observed 
-    transport mechanisms which we conjecture will be the same regardless of
-    concentration.
+    we are focused on the underlying solute-membrane interactions that lead to
+    the observed transport mechanisms which we conjecture will be the same 
+    regardless of concentration.
     \item We will not study the chemical potential of solutes in the pores, which
@@
 
-  \subsection{Molecular Dynamics Simulations}
-
-  \subsubsection*{System Setup}
+  \subsection*{System Setup}
 
@@
 
+  %BJC: reference to supporting info with more details on water partition
+  %BJC: or should that go in the main body results?
   We observed that water partitions into the tail region of our system and therefore
@@
 
-  \subsubsection*{Radial Distribution Functions}
+  \subsection*{Mean Squared Displacment}
+
+  \subsection*{Radial Distribution Functions}
 
@@
 
-  \subsubsection*{Coordination number}
+  \subsection*{Coordination number}
 
@@
 
-  We will answer the questions posed in the introduction in a general 
-  sense before addressing them with respect to specific molecules.
-
-  % BJC: seems right to summarize overarching mechanisms observed first  
-  On the timescales simulated in our study, solutes exhibit subdiffusive
-  transport behavior as evidenced by their sublinear MSD curves. 
-  \begin{itemize}  
-	\item As an example, the MSD curve for ethanol is plotted in 
-	Figure~\ref{fig:example_msd}.
-  \end{itemize}
-
-  \noindent All solutes exhibit hop diffusion, characteristic of a continuous time random walk.
-  \begin{itemize}
-  	\item Figure~\ref{fig:example_ztraces} shows the $z$-coordinate versus time of
+  We have gained a clearer picture of the general transport properties exhibited by
+  this system through the collective study of all solutes. We will first answer the
+  questions posed in the introduction in a general sense before addressing them with
+  respect to specific molecules where exceptions occur.
+
+  On the timescales simulated in our study, we observe subdiffusive behavior.  
+  \begin{itemize}  
+    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
   	3 representative ethanol centers of mass.
   	\item There are clear periods of entrapment separated by relatively large hops.
+	\item The MSD calculated based on all ethanol molecules is plotted in Figure~\ref{fig:example_msd}
+	and is sublinear.
+	\item The long periods of entrapment likely lead to this sublinear, and thus
+	subdiffusive, behavior.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
+  \caption{}\label{fig:example_ztraces}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\linewidth]{example_msd.pdf}
+  \caption{}\label{fig:example_msd}
+  \end{subfigure}
+  \caption{}\label{fig:qualitative_mechanisms}
+  \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  Mathematical modeling 
+  All solutes exhibit hop diffusion, characteristic of a continuous time random walk.	
+  \begin{itemize}
   	\item The length of entrapment follows a power law distribution 
@@
   \end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-03-02 Ben_Manuscripts/transport/Outline.tex
Outline updates

@@
 %  framework for studying this system in even greater detail.
-  There are a number of questions we wish to address in order to characterize
+  \noindent There are a number of questions we wish to address in order to characterize
   transport in this system.
@@
 
-   	\item What transport mechanisms do we observe?
+   	\item What transport mechanisms do we observe? \label{question:mechanisms}
 
@@
 
-  	\item How do molecules, including water, partition within the pores?
+  	\item How do molecules, including water, partition within the pores? \label{question:partition}
 
@@
   	\item Can we describe the transport mechanisms using pre-existing 
-  	mathematical models.
+  	mathematical models. \label{question:math}
 
@@
   	\item How can we modify the current monomers in order to enhance
-  	solute-specific separations?
+  	solute-specific separations? \label{question:math}
 
@@
 
-  There are number of questions this study is not intended to answer.
+  \noindent There are also a number of questions this study is not intended 
+  to answer.
   \begin{itemize}
@@
     could give us a better understanding of equilibrium solute partitioning.
-    However, this information will not greatly enhance our understanding of 
+    This information will not greatly enhance our understanding of 
     mechanistic details in various membrane regions.
@@
 
-  We equilibrated an initial solvated configuration before adding solutes.
+  \noindent We equilibrated an initial solvated configuration before adding solutes.
   \begin{itemize}
@@
 
-  We added 6 solute molecules to each pore of the equilibrated cross-linked
+  \noindent We added 6 solute molecules to each pore of the equilibrated cross-linked
   configuration.
@@
 
-%  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}
-%
-%  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
-%  behavior, a type of anomalous diffusion. 
-%  \begin{itemize}
-%  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
-%  	does not grow linearly with time, rather it is of the form:
-%	\begin{equation} 
-%	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
-%	\label{eqn:msd_form}
-%	\end{equation} 
-%	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
-%	generalized diffusion coefficient.
-%	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
-%	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
-%	motion respectively.
-%  \end{itemize}
-%
-%  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
-%  of the simulated trajectories.
-%  \begin{itemize}
-%	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
-%	position~\cite{meroz_toolbox_2015} and can be written as
-%	\begin{equation}
-%	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
-%	\label{eqn:ensemble_msd}
-%	\end{equation}
-%%	\item The average MSD calculated in this way recovers the form of
-%%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
-%	\item The time-averaged MSD measures the displacement between all possible time lags
-%	and can be written as
-%	\begin{equation}
-%	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
-%	\end{equation}
-%	where $\tau$ is the time lag and T is the length of the
-%	trajectory~\cite{meroz_toolbox_2015}. 
-%%	\item The time-averaged MSD becomes linear in our simulations,
-%%	therefore we can fit a line to its slope in order to estimate the macroscopic
-%%	diffusivity of the particle.
-%	%BJC: this needs more justification. Not many people have done it
-%	%BJC: could also not report them as diffusivities. Comparison of total MSD
-%	% should give same information
-%	% Linear region probably exists because dwell times on the order of large lag times
-%	% become negligible
-%  \end{itemize}
-%  
+  \subsection*{Mean Squared Displacement}\label{method:MSD}
+
+  \noindent We measured the time-averaged mean squared displacement (MSD)
+  of the centers of mass of each solute over the course of 1 $\mu$s MD 
+  simulations using Equation~\ref{eqn:tamsd}.
+  \begin{itemize}
+    \item \begin{equation}
+	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
+	\label{eqn:tamsd}
+	\end{equation}
+	where $\tau$ is the time lag and T is the length of the
+	trajectory~\cite{meroz_toolbox_2015}. 
+	\item Generally, the MSD grows according to Equation~\ref{eqn:msd_form},
+	\begin{equation} 
+	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
+	\label{eqn:msd_form}
+	\end{equation} 
+	\item where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
+	generalized diffusion coefficient.
+	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
+	$\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
+	motion respectively.
+	\item In practice, $\alpha$ corresponds to the growth of the \textit{ensemble}
+	MSD given by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
+	\begin{equation}
+	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
+	\label{eqn:ensemble_msd}
+	\end{equation}
+	\item The ensemble MSD is calculated with respect to a reference position and
+	hence carries some dependence on its starting point.
+	\item The time-averaged MSD averages over all possible time lags of a given 
+	length, effectively eliminating any initial configuration dependence and generating
+	an increased number of observations. 
+	\item For ergodic systems, both types of MSDs will be equal.
+	\item Since we have a small number of solutes with which to generate statistics
+	and because we are not calculating values for $\alpha$ in this particular study,
+	we will only use the time-averaged MSD.
+  \end{itemize}
+
+  %BJC: need to word this differently since I haven't talked about CTRW yet
+  \noindent We fixed the length of each simulated trajectory so that we could compare
+  the total MSD between different solutes without the influence of the ageing phenomenon.
+  \begin{itemize}
+	\item Ageing is defined by the tendency of the average MSD to decrease
+	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
+	\item The maximum measured dwell time can be no longer than the total length
+	of a simulated trajectory. 
+	\item As measurement time or trajectory length is increased, longer dwell times
+	are incorporated into the calculation, lowering the average MSD. (See supporting
+	info for demonstration)
+	\item Because the MSDs are non-linear and because of the ageing phenomenon, we
+    did not attempt to calculate a diffusion constant as one might for a Brownian
+    particle with a linear MSD.
+	\item Instead, the reported values for MSD represent the average MSD for a given
+	solute after a 400 ns time lag.
+  \end{itemize}
+
 %  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
@@
 %  \end{itemize}
-%  
+
 %  \noindent We believe that solutes in the system studied here exhibit subordinated 
@@
 %  \end{itemize}
-%
-%  \noindent We can characterize a CTRW process using the parameters which describe its
-%  dwell time and hop length distribution.
-%  \begin{itemize}
-%	\item We used the \texttt{ruptures} python package in order to identify
-%	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
-%	details on chosen parameters. i.e. type of cost function, cost function penalty
-%	tolerance, number of dimensions used)
-%	\item The corresponding hop lengths and dwell times between break points were 
-%	used to construct empirical distributions.
-%	\item For solutes in our system, the distribution of hop lengths is
-%	well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
-%	metzler_anomalous_2014,neusius_subdiffusion_2009}
-%	\item We are most interested in the standard deviation, $\sigma$, of the 
-%	hop length distribution.
-%	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
-%	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
-%	\item Because we are limited to taking measurements at discrete values
-%	dictated by the output frequency of our simulation trajectories, we fit the
-%	empirical dwell times to a discrete power law distribution whose maximum
-%	likelihood $\alpha$ parameter we calculated by maximizing the following
-%	likelihood function: 
-%        \begin{equation}
-%	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
-%	\beta\sum_{i=1}^{n} \text{ln}~x_i 
-%	\label{eqn:powerlaw_likelihood}
-%	\end{equation}
-%	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
-%	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
-%	where $x_{min}$ is the smallest measured value of
-%	$x_i$.~\cite{clauset_power-law_2009} 
-%	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
-%	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
-%  \end{itemize}
-%  
-%  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
-%  $H = \beta/2$.
-%  \begin{itemize}
-%  	\item Brownian motion is recovered for $H = 0.5$
-%	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
-%    \begin{equation}
-%	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
-%	\label{eqn:autocovariance}
-%	\end{equation}
-%	where $k$ is the number of increments between hops.
-%	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
-%	to the empirically measured autocovariance function.
-%	\item We used statistical bootstrapping to generate a distribution of $H$ 
-%	values. %BJC: can provide more detail in supporting or just reference python script
-%  \end{itemize}
-%
-%%  We generated distributions of parameters for the dwell time and hop length
-%%  distributions using statistical bootstrapping.
-%%  \begin{itemize}
-%%	\item For each type of distribution, we randomly selected $n$ data points from the empirical
-%%	distribution with replacement.
-%%	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
-%%  \end{itemize} 
-%
-%%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
-%%  magnitude longer than our molecular simulations.
-%  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
-%  \begin{itemize}
-%	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
-%	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
-%	distributions.
-%	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
-%	the last data point so that the total time exactly equaled 1 $\mu$s. 
-%    \item Valid comparisons are only possible between fixed length sFBM simulations. The
-%    power law dwell time behavior gives rise to the aging phenomenon, embodied by
-%    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
-%    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
-%% Following probably better suited for supporting information, if included at all
-%%	\item We randomly sample Gaussian hop lengths using the
-%%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
-%%	\item We randomly sampled dwell times from a discrete power law
-%%	distribution based on the recommendations of Clauset et
-%%	al.~\cite{clauset_power-law_2009}: 
-%%	\begin{equation}
-%%	x = \lfloor
-%%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
-%%	\label{eqn:discrete_powerlaw_draws}
-%%	\end{equation}
-%%	where $r$ is randomly drawn from a uniform distribution which we simulated
-%%	with \texttt{numpy.random.uniform}.
-%%	\item We found that thermal noise does not significantly influence the MSD and
-%%	therefore did not add any noise to the simulated trajectories. (See supporting info)
-%  \end{itemize}
-%
-%%BJC: probably don't need to explain this in great detail
-%%  \noindent We fixed the length of each simulated trajectory so that we could compare the total
-%%  MSD between different solutes without the influence of the ageing phenomenon.
-%%  \begin{itemize}
-%%	\item Ageing is defined by the tendency of the average MSD to decrease
-%%	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
-%%	\item The maximum measured dwell time can be no longer than the total length
-%%	of a simulated trajectory. 
-%%	\item As measurement time or trajectory length is increased, longer dwell times
-%%	are incorporated into the calculation, lowering the average MSD. (See supporting
-%%	info for demonstration)
-%%	\item We can achieve consistent total MSDs with low uncertainty for
-%%	simulated trajectories created with a given set of parameters if we fix the
-%%	trajectory length (as opposed to total number of steps).  
-%%  \end{itemize}
-
-  \subsection*{Mean Squared Displacment}
-
-  \subsection*{Radial Distribution Functions}
+
+  \subsection*{Dwell and Hop Length Distributions}\label{method:hops_and_dwells}
+
+  \noindent We measured the distribution of dwell times and hop lengths in order to test
+  the hypothesis that solutes follow a CTRW process.
+  \begin{itemize}
+	\item We used the \texttt{ruptures} python package in order to identify
+	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
+	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
+	function, cost function penalty	tolerance, number of dimensions used)
+	\item The corresponding hop lengths and dwell times between break points were 
+	used to construct empirical distributions.
+  \end{itemize}
+
+  \subsection*{Radial Density Functions}
 
@@
 	pore centers.
-	\item We construct the splines by dividing the membrane into 20 slices
+	\item We construct the splines by dividing the membrane into 10 slices
 	in the $z$-direction. Within each slice, we calculate the location of 
@@
 	\item When calculating the RDF, the radial distance from the pore center
-	is based on the distance between the solute center-of-mass and the ($x$, $y$)
-	coordinates of appropriate point on the spline.
+	is based on the distance between the solute center-of-mass and the linearly
+	interpolated ($x$, $y$)	coordinates of the pore center calculated based
+	on the spline.
+  \end{itemize}
+
+  \subsection*{Identification of Hydrogen Bonds}
+
+  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
+  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
+  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
+    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
+    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
+    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
+    % from Debye-Waller factors
+  \begin{itemize}
+    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
+    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
+	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
+    \item The definition of Luzar and Chandler is easily visualized for trajectories using
+    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
+    package which allows us to directly check the validity of identified hydrogen bonds.
+    %BJC: might need to update this if something better exists for nitrogen 
   \end{itemize}
@@
 
-  \subsection*{Governing Mechanisms}\label{section:mechanism_overview}
-
-  We have gained a clearer picture of the general transport properties exhibited by
-  this system through the collective study of all solutes. We will first answer the
-  questions posed in the introduction in a general sense before addressing them with
-  respect to specific molecules where exceptions occur.
-
-  On the timescales simulated in our study, we observe subdiffusive behavior.  
+  \subsection*{Structure and Transport of Membrane Components}\label{section:membrane_components}
+
+  %BJC: Probably do analysis on pure water system for this section.
+
+  In contrast to our previous work with a solvent-free version of this membrane, the pore
+  region of the 5 and 10 wt \% water systems are primarily filled with water and sodium
+  ions.
+  \begin{itemize}
+    \item In dry systems, the pore center is densely filled with sodium ions and 
+    head groups (See Ref~\cite{coscia_understanding_2019}).
+    \item Figure~\ref{fig:component_densities} plots the densities of each
+    membrane component.
+    \item Water is densest at the center of each pore. 
+    \item Sodium ions are densest within the pore region, which we define as the
+    space between the pore center and the peak head group density.
+    \item The peak density of sodium ions is not at the pore center in either case
+    likely because they are still loosely associated with the monomer's 
+    carboxylate head groups.
+  \end{itemize}
+
+  \noindent Pores in the 10 wt\% water system are wider and less crowded by monomers than
+  those in the 5 wt\% water system.
+  \begin{itemize}
+    \item The peak head group density of 10 wt\% water systems is about 0.2 nm
+    further from the pore center than the 5 wt\%
+    \item The 5 wt \% water system has a non-negligible amount of tail group atoms
+    that occupy the pore center.
+  \end{itemize}
+
+  %BJC: I'm not sure if would be better to normalize the densities so that the
+  % shape of the sodium density is more pronounced
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
+  \caption{5 wt\% water}\label{fig:component_density_5wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
+  \caption{10 wt\% water}\label{fig:component_density_10wt}
+  \end{subfigure}
+  \caption{The radial densities of various monomer components paint a picture of the
+  pore topology where the pore centers are primarily composed of water and sodium ions.
+  The 5 wt \% system (a) appears to be much more crowded by monomers than the 
+  10 wt \% system (b). Head groups in (a) are densest closer to the pore center than
+  in (b). A small amount of tail components find their way close to the pore center 
+  of the 5 wt \% system. }\label{fig:component_densities}
+  \end{figure}
+
+  The MSD of sodium and water become linear on long timescales.
+  \begin{itemize}
+    \item
+  \end{itemize}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{water_msd_comparison.pdf}
+  \caption{Water}\label{fig:water_msd_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{na_msd_comparison.pdf}
+  \caption{Sodium Ions}\label{fig:na_msd_comparison}
+  \end{subfigure}
+  \caption{}\label{fig:msd_comparison}
+  \end{figure}
+
+  Sodium coordinates with water.
+
+  \noindent The diffusion constant of water is about 50 times faster than sodium.
+  \begin{itemize}
+    \item In a dilute sodium chloride solution, the diffusivity of sodium
+    is about 4 times slower than water.
+    \item The carboxylate groups, whose oxygen atoms each have a charge of -0.822
+    keep the positively charged sodium ions relatively close and restricts their
+    motion.
+  \end{itemize}
+
+  \subsection*{Mechanisms Governing Small Solute Transport}\label{section:mechanism_overview}
+
+  \noindent The MSDs for the solutes studied in this work span a moderate range. 
+  \begin{itemize}
+    \item We plotted the 400 ns time-lag MSD for each solute in Figure~\ref{fig:all_msds}.
+  	\item The fastest solute, methanol, has an MSD over 20 times greater than
+  	the slowest, dimethyl formamide. 
+  \end{itemize}
+
+  \noindent The MSDs are not a monotonic function of solute size.
+  \begin{itemize}
+  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:all_msds}.
+  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
+  	than half of all solutes studied. 
+  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
+  	\item Transport is clearly affected by factors other than molecular size. 
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}  % include bar plot of MW to show it's non-monotonic
+  \caption{}\label{fig:all_msds}
+  \end{subfigure}
+  \begin{subfigure}{0.5\textwidth}
+  \includegraphics[width=\textwidth]{msd_radius.pdf} 
+  \caption{}\label{fig:msd_radius}
+  \end{subfigure}
+  \caption{}\label{fig:msds}
+  \end{figure}
+
+%  We have gained a clearer picture of the general transport properties exhibited by
+%  this system through the collective study of all solutes. We will first address the
+%  questions posed in the introduction in a general sense before addressing them with
+%  respect to specific molecules, where exceptions occur.
+%  \bigskip
+
+  \noindent On the timescales simulated in our study, we observe subdiffusive behavior.
+  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
   \begin{itemize}  
@@
 
+  Solutes partition out of the pore into the head group region and beyond which
+  may lead to radially dependent transport mechanisms.
+  \begin{itemize}
+    \item It is clear from Figure~\ref{fig:example_ztraces} that the longest 
+    periods of entrapment generally occur when solutes are far from the pore
+    center.
+    \item There is a high resistance to movement in the dense head group and
+    tail regions.
+    \item When hops occur, and where there is the most $z$-positional noise, 
+    solutes are generally close to the pore center.
+    %BJC: need a radial density of head groups, tails, water etc.
+    \item Solutes can move relatively freely when they enter the pore region
+    which is primarily composed of water molecules.
+  \end{itemize}
+
   \begin{figure}
@@
   \end{subfigure}
-  \caption{}\label{fig:qualitative_mechanisms}
+  \caption{All solutes show subdiffusive transport behavior inside the membrane's
+  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
+  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
+  In general, the longest dwell times occur when solutes are situated far from the
+  pore center and the hops occur when solutes are close to the pore center. (b) The
+  time-averaged MSD of ethanol is not linear which suggests transport is governed 
+  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
   \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  Mathematical modeling 
-  All solutes exhibit hop diffusion, characteristic of a continuous time random walk.	
+  In addition to solute trapping in dense monomer regions, we observe a second
+  trapping mechanism caused by preferential hydrogen bonding between 
+  hydrogen bond donor solutes and monomer carboxylate groups. 
+  \begin{itemize}
+    \item Of the time spent donating hydrogen atom(s), x \% of the hydrogen
+    bonds occur between solutes and carboxylate groups as opposed to solutes
+    with water. 
+    \item This shows a high perference for the carboxylate anions since there
+    are 5 times more water molecules in the system.
+    \item The carboxylate oxygen atoms have a slightly higher partial negative
+    charge than water molecules.
+    \item Additionally, on average, each sodium ion is coordinated to 3 water
+    molecules. Roughly all of the water in the pore region is usually coordinated
+    to a sodium ion which decreases their availability to solutes.
+  \end{itemize}
+
+  \noindent The hopping and trapping mechanism exhibited by all solutes is characteristic of
+  a continuous time random walk (CTRW) model.	
   \begin{itemize}
@@
   	\item Power law distributed dwell times are responsible for the ageing phenomenon
-  	which causes the MSD curve to decrease with increasing measurement time as longer
-  	dwell times get sampled.
-  \end{itemize}
-
-  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
+  	which causes the slope of the MSD curve to decrease with increasing measurement
+  	time because longer dwell times are sampled.  %BJC: might need to reword this a bit 
+ 	\item Although these observed distributions strongly support a CTRW model, the time-averaged
+ 	MSD of a pure CTRW should be linear which is not the case.~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
+  \end{itemize}
+
+%  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
+  \noindent Transport may be better described by a subordinated fractional brownian motion 
+  (sFBM) model.
   \begin{itemize}
@@
   	\item The negative autocovariance at low values of k indicates anti-correlation
-  	between steps. 
+  	between hops. 
   	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
@@
   	\item Therefore, we believe transport can be described as subordinated fractional Brownian
-  	motion where the leading process is a CTRW with hops that are dictated by the parent
+  	motion where the leading process is a CTRW with hops whose direction is dictated by the parent
   	process, FBM.
@@
   	with an sFBM model
-  \end{itemize}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% BJC: first iteration of figure after this before I decided to include a hop length and dwell time distribution
-%  \begin{figure}
-%  \centering
-%  \includegraphics[width=\textwidth]{msd_ztrace_acf.pdf}
-%  \caption{}\label{fig:msd_ztrace_acf}
-%  \end{figure}
+  	\item We will draw on these observations only in a qualitative sense for the remainder of this work.
+  \end{itemize}
+
+  %BJC: seems like the MSD becomes linear at long times. Perhaps due to loss of memory with time.
 
@@
   \centering
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\linewidth]{example_msd.pdf}
-  \caption{}\label{fig:example_msd}
-  \end{subfigure}
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\linewidth]{example_ztraces.pdf}
-  \caption{}\label{fig:example_ztraces}
-  \end{subfigure}
-  \par\medskip
   \begin{subfigure}{0.325\textwidth}
@@
   \end{subfigure}
-  \caption{All solutes show subdiffusive transport behavior inside the membrane's
-  nanopores, similar to that exhibited by ethanol. (a) The time-averaged MSD of 
-  ethanol is not linear which suggests transport is governed by an anomalous 
-  subdiffusion process. (b) The $z$-coordinate trace of 3 representative ethanol
-  COMs shows clear periods of entrapment separated by hops. (c) The distribution
-  of dwell times follows a power law. (d) The distribution of hop lengths appears
-  Gaussian. (e) Hops are anti-correlated to their previous hop as indicated by the
-  negative value of the autocovariance function at $k$ = 1.}\label{fig:examples}
+  \caption{(a) The distribution of dwell times resembles a power law distribution. 
+  (b) The distribution of hop lengths appears Gaussian. (c) Hops are anti-correlated
+  to their previous hop as indicated by the negative value of the autocovariance 
+  function at $k$ = 1.}\label{fig:examples}
   \end{figure}
 
-  % BJC: would it be better to report as a fraction of water MSD?
-  % BJC: need MSDs of 5 wt % systems here too. Can narrow to study of 10 wt % systems after
-  \noindent We calculated the time-averaged MSD of each solute in the set over the
-  course of 1 $\mu$s MD simulations. 
-  \begin{itemize}
-    \item Because the MSDs are non-linear and because of the ageing phenomenon, we
-    did not attempt to calculate a diffusion constant as one might for a Brownian
-    particle with a linear MSD.
-	\item Instead, the MSD values plotted in Figure~\ref{fig:all_msds} represent the
-	average MSD of each solute after a 400 ns time lag.
-  \end{itemize}
-
-%  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}
-%
-%  Solutes in systems with lower water content exhibit lower diffusion coefficients.
+%  \noindent The MSDs in Figure~\ref{fig:all_msds} are a strong function of two solute 
+%  trapping mechanisms.
 %  \begin{itemize}
-%	\item Pores are more crowded when there is less water (show RDFs of each)
-%	\item Not a linear function of pore size - radius increase by x, D increases by y
-%	\item Larger influence on bigger molecules
+%  	\item Solutes that are hydrogen bond donors can be stabilized through hydrogen bonds
+%  	with one of the five oxygen atoms attached to each monomer head group. 
+%  	\item In a separate interaction, solutes can become kinetically trapped between or behind
+%  	monomer head groups. These interactions likely lead to the observed anti-correlated
+%  	hopping	behavior.
+%  	\item Generally, both mechanisms affect each solute to varying degrees.
 %  \end{itemize}
 
-  \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{all_tamsds.pdf}  % include bar plot of MW to show it's non-monotonic
-  \caption{}\label{fig:all_msds}
-  \end{figure}
-
-  \noindent The MSDs are not a monotonic function of solute molecular weight.
-  \begin{itemize}
-  	\item We plotted the solute molecular weights alongside their MSDs in Figure~\ref{fig:all_msds}.
-  	\item Transport is clearly affected by factors other than molecular weight. 
-  	\item Tetrose, our third heaviest solute, has an MSD higher than more than half of
-  	all solutes studied. 
-  	\item The three slowest solutes have lower molecular weights than 8 faster solutes.
-  \end{itemize}
-
-  \noindent The MSDs in Figure~\ref{fig:all_msds} are a strong function of two solute 
-  trapping mechanisms. % by which solutes become trapped.
-  \begin{itemize}
-  	\item Solutes that are hydrogen bond donors can be stabilized through hydrogen bonds
-  	with one of the five oxygen atoms attached to each monomer head group. 
-  	\item In a separate interaction, solutes can become kinetically trapped between or behind
-  	monomer head groups. These interactions likely lead to the observed anti-correlated
-  	hopping	behavior.
-  	\item Generally, both mechanisms affect each solute to varying degrees.
-  \end{itemize}
-
-  %BJC: somewhere need to say why solutes preferentially hbond with carboxylate groups -- is this real
-
   %BJC: This will need updating once all the rest of outline is written.
-  \noindent The degree to which solutes are influenced by each entrapment mechanism
-  is a complex function of a solute's size, shape, and polarity.
-  \begin{itemize}
-    \item In general, solutes can move fastest in the pore center, where
-    there is comparatively little resistance to diffusion.
-	\item The 5 fastest solutes in our study have a low molecular weight and
-	spend a significant amount of time in the pore center. They are only slowed
-	by hydrogen bonds with monomer carboxylate groups.
-	\item Bulky solutes with many hydrogen bond donating groups, like glycerol,
-	spend most of their time in the pore center, but their large size combined
-	with a higher solute-head group hydrogen bond frequency, makes their dynamics slow. 
-    \item Solutes with high hydrophobic character tend to partition into the 
-    head group region where entrapment occurs.
-    \item We observe low MW solutes with lower-than-expected MSDs because they
-    spend more time trapped between monomer head groups due to low water
-    solubility.
-    \item Small, planar molecules, without the ability to donate hydrogen bonds, like acetone,
-    exhibit some of the slowest MSDs. Their flat geometry and small size makes it easy for 
-    them to get lodged deep between head groups.
-  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
-  	mechanisms, with anticorrelated hops between each period of immobility due to 
-  	obstructions.
-  \end{itemize}
+%  \noindent The degree to which solutes are influenced by each entrapment mechanism
+%  is a complex function of a solute's size, shape, and polarity.
+%  \begin{itemize}
+%    \item In general, solutes can move fastest in the pore center, where
+%    there is comparatively little resistance to diffusion.
+%	\item The 5 fastest solutes in our study have a low molecular weight and
+%	spend a significant amount of time in the pore center. They are only slowed
+%	by hydrogen bonds with monomer carboxylate groups.
+%	\item Bulky solutes with many hydrogen bond donating groups, like glycerol,
+%	spend most of their time in the pore center, but their large size combined
+%	with a higher solute-head group hydrogen bond frequency, makes their dynamics slow. 
+%    \item Solutes with high hydrophobic character tend to partition into the 
+%    head group region where entrapment occurs.
+%    \item We observe low MW solutes with lower-than-expected MSDs because they
+%    spend more time trapped between monomer head groups due to low water
+%    solubility.
+%    \item Small, planar molecules, without the ability to donate hydrogen bonds, like acetone,
+%    exhibit some of the slowest MSDs. Their flat geometry and small size makes it easy for 
+%    them to get lodged deep between head groups.
+%  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
+%  	mechanisms, with anticorrelated hops between each period of immobility due to 
+%  	obstructions.
+%  \end{itemize}
 
@@
 
-  We will revisit these observations in the the context of specific groups of 
+  We will revisit our observations in the the context of specific groups of 
   molecules in the discussion that follows.
@@
 
-  \subsection*{Transport of Water}
-
-  The MSD of water is a weak function of the solute residue disolved in
-  the pores.
-  \begin{itemize}
-  	\item Large molecules like glycerol and ribose obstruct the movement
-  	of water molecules forcing them to have lower MSDs
-  	\item I don't know why the MSD is fast in the fastest systems or why DMSO is slow.
-  	\item Sulfur containing compounds have slowest water transport
-  	\item How do 24 solute molecules have such a drastic effect on water motion
-  \end{itemize}
-
-  % BJC: MSDs only calculated for water molecules that spend > 95 % of their
-  % time in the pore. Pore region / tail region cutoff is at 1.5 nm (approximate location of lowest radial water density) 
-  \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{water_msd.pdf}
-  \caption{}\label{fig:water_msd}
-  \end{figure}
+% BJC: Move to supporting
+%  \subsection*{Transport of Water}
+%
+%  The MSD of water is a weak function of the solute residue disolved in
+%  the pores.
+%  \begin{itemize}
+%  	\item Large molecules like glycerol and ribose obstruct the movement
+%  	of water molecules forcing them to have lower MSDs
+%  	\item I don't know why the MSD is fast in the fastest systems or why DMSO is slow.
+%  	\item Sulfur containing compounds have slowest water transport
+%  	\item How do 24 solute molecules have such a drastic effect on water motion
+%  \end{itemize}
+%
+%  % BJC: MSDs only calculated for water molecules that spend > 95 % of their
+%  % time in the pore. Pore region / tail region cutoff is at 1.5 nm (approximate location of lowest radial water density) 
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=\textwidth]{water_msd.pdf}
+%  \caption{}\label{fig:water_msd}
+%  \end{figure}
 
@@
 
+  % General framework for following sections
+  % The MSDs are in this order. This is counterintuitive / makes sense for some reason
+  % Here are the RDFs
+  % Here is some other feature that helps explain things.
+
   \subsection*{Transport of Simple Alcohols}
@@
   their molecular weight, however, methanol travels faster than expected.  %BJC: find approximate relationship between MW and mobility
+  \begin{itemize}
+    \item The MSD of ethanol, propanol and butanol descend approximately
+    linearly as expected form the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
+    \item However, methanol travels considerably faster based on this relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
+  \end{itemize}
+
+  Methanol moves fast because it has the highest radial density near the pore center where
+  the largest hops occur.
   \begin{itemize} 
@@
   with the monomer head groups, but with varying preference towards hydrogen bonds with
-  the monomer carboxylate oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds}).
+  the monomer carboxylate oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds}) caused
+  by increasing hydrophobic character.
   \begin{itemize}
@@
   	\item This is largely due to the more highly crowded environment surrounding the ether
-  	oxygen atoms.
+  	oxygen atoms combined with their lower partial charges.
   	\item Butanol shows the largest preference towards hydrogen bonds with carboxylate 
@@
   	monomers, with hydrophilic components point towards the pore centers.
+  	\item When solutes are buried in the pore walls, their MSDs are shorter.
   \end{itemize}
@@
   \centering
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols.pdf}
+  \caption{}\label{fig:msd_radius_simple_alcohol_rdf}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
   \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.45\textwidth}
   \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.45\textwidth}
   \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing butanol with highlighted O and C
@@
 
-  Transport is both facilitated and hindered by additional solute hydroxyl groups.
+  The order of the MSDs of solutes in this grouping are roughly consistent with 
+  their size, however propylene glycol moves exceptionally slow.  %BJC: or tetrose and glucose are exceptionally fast
+  \begin{itemize}
+  	\item Ethylene glycol has the highest MSD followed by tetrose
+  	and glycerol, whose MSDs are similar, propylene glycol, the second smallest
+  	solute of this set, and finally ribose.
+  \end{itemize}
+
+  Transport is both facilitated and hindered by additional solute hydroxyl groups
+  due to their influence on radial density and hydrogen bond frequency.  	
   \begin{itemize} 
     \item Extra hydroxyl groups cause solutes to favor the water-rich pore region.
-    where there is the least hindrance to movement.
+    where there is the least hindrance to movement (See Figure~\ref{fig:polyols_rdf}).
+    \item Tetrose, ribose and glycerol are densest close to the pore center. This is 
+    likely a result of their hydrophilicity and large size which prevents them from
+    partitioning into the head group region.
     \item However, these extra hydroxyl groups facilitate a larger number of 
     hydrogen bond interactions that work to hold solutes in place (See Figure~\ref{fig:multi_hbonds}).
-    \item At the same time, solute molecular weight increases, which inherently
-    causes them to move more slowly.
-    \item Ethylene glycol, the fastest solute in this grouping (and second fastest
-    overall), obtains the best balance of both effects.
+    \item It has been observed that hydrogen bonding in a system will generally
+    reduce diffusivity~\cite{srinivas_computer_1999}
+%    \item Ethylene glycol, the fastest solute in this grouping (and second fastest
+%    overall), obtains the best balance of both effects.
   \end{itemize}
@@
     head groups simultaneously.
+    \item Hydrogen bonds act as a kind of molecular glue which holds solutes in place, 
+    especially when there are many, however proximity to the pore center partially 
+    compensates for this effect in the cases of glycerol and tetrose.
   \end{itemize}
@@
   \centering
+  \begin{subfigure}{0.45\textwidth}
+  % BJC: This might be better cut off at y ~ 0.6 and then provide an inset with full RDFs
+  \includegraphics[width=\linewidth]{polyols_rdf.pdf}
+  \caption{}\label{fig:polyols_rdf}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
   \includegraphics[width=\linewidth]{multi_hbonds.pdf}
+  \caption{}\label{fig:multi_hbonds}
+  \end{subfigure}
+  % BJC: this subfigure is probably best suited for the supporting information.
+  \begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
+  \caption{}\label{fig:dwell_hop_PG_GCL}
+  \end{subfigure}
   \caption{The number of hydrogen bond interactions between solutes and monomers increases
@@
 
-  Between the two diols, ethylene glycol moves significantly faster than propylene glycol
-  due to propylene glycol's affinty for the monomer head groups.  
-  \begin{itemize}
-  	\item The distribution of each solute's dwell time and hop length distributions shows that
-  	ethylene glycol has shorter dwell times and longer hop lengths, which combine to create a 
-  	relatively fast MSD. 
-  	%BJC: number of PG vs ethylene glycol that enters middle -- I don't think this will be any different than density function
+  Of the two diols, ethylene glycol moves significantly faster than propylene glycol
+  due to propylene glycol's affinity for the monomer head groups.  
+  \begin{itemize}
+    \item Combined with an increase in size, the addition of a single methyl group to ethylene glycol
+    increases propylene glycol's hydrophobic character and causes it to favor positions
+    near monomer head groups.
     \item Both diols have comparable densities close to the pore center, however propylene glycol's
     density has a large peak near the monomer head groups relative to ethylene glycol.
-    \item Combined with an increase in molecular weight, the addition of a single methyl group
-    increases the molecule's hydrophobic character and causes propylene glycol to favor positions
-    near monomer head groups.
-    \item This causes propylene glycol to form more highly stablized hydrogen bonds with
-    carboxylate groups, explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
-  \end{itemize}
-
-  % BJC: figure does not represent total number of hops (PG has less hops)
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=\linewidth]{dwell_hop_PG_GCL.pdf}
-  \caption{}\label{fig:dwell_hop_PG_GCL}
-  \end{figure}
-
-  Solutes with three or more hydroxyl groups have the highest density
-  at the pore center which contributes to overall faster than expected transport.
-  \begin{itemize}
-  	\item These molecules are highly water soluble but relatively large
-  	\item They can easily hydrogen bond in multiple locations.
-  	\item Their large size and high hydrogen bonding capability prevents them
-  	from having larger MSDs.
-  \end{itemize}
+    \item Propylene glycol can form more highly stablized hydrogen bonds with carboxylate groups,
+    explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
+    \item These observations are further reflected in its dwell and hop length distributions
+    (See Figure~\ref{fig:dwell_hop_PG_GCL}).
+    \item Propylene glycol exhibits longer dwell times and a narrower distribution of 
+    hop lengths than ethylene glycol. 
+    \item Somewhat counterintuitively, there is a relatively high density of ethylene
+    glycol molecules beyond the head group region. This likely contributes to the relatively
+    large error bars on its MSD in Figure~\ref{fig:all_msds}. 
+    %BJC: can show figure of radial density colored with hop lengths
+    \item This implies that hops performed by ethylene glycol must be considerably larger
+    than those by propylene glycol in order to result in consistently larger MSD values.
+  \end{itemize}
+
+%  Solutes with three or more hydroxyl groups have the highest density
+%  at the pore center which contributes to overall faster than expected transport.
+%  \begin{itemize}
+%  	\item These molecules are highly water soluble but relatively large
+%  	\item They can easily hydrogen bond in multiple locations.
+%  	\item Their large size and high hydrogen bonding capability prevents them
+%  	from having larger MSDs.
+%  \end{itemize}
 
@@
   \begin{itemize}
-    \item Urea, Acetic Acid, Acetamide and Acetone are all characterized by a carbonyl group
+    \item Urea, acetic acid, acetamide and acetone are all characterized by a carbonyl group
     with two attached heavy atoms. 
-    \item All have approximately the same molecular weight and are planar molecules due to
-    the sp2 hybridization of the carbonyl group.
-    \item The fastest solute of this grouping, Urea (comparable to Acetic Acid too), has an
-    MSD comparable to that of ethylene glycol while the slowest, Acetone, has an MSD one 
-    third of that of Urea.
-  \end{itemize}
+    \item All are similar in size and are planar molecules due to the sp2 hybridization of
+    their carbonyl group.
+    \item The fastest solute of this grouping, acetic acid (comparable to urea), is about
+    3 times faster than the slowest, acetone, but only about 10 \% smaller.
+  \end{itemize}
+
+  The MSD of the solutes descend in order of their density close to the pore center.
+  \begin{itemize}
+    \item As shown in the radial density functions (Figure~\ref{fig:ketones_rdf}), 
+    Acetic has a fairly uniform and high density within the pore region.
+    \item Acetone spends relatively little time near the pore center with its
+    peak density nearest the peak head group density.
+  \end{itemize}
+
+  The amides, urea and acetamide hydrogen bond with head groups relatively infrequently.
+  \begin{itemize}
+    \item Acetic acid hydrogen bonds with head groups nearly 20 times as frequently.
+    \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
+  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
+    \item The peaks in their radial density are closer to the pore center than 
+    other solutes that hydrogen bond with carboxylate groups (see 
+    Figure~\ref{fig:simple_alcohol_rdf} for example).
+  \end{itemize}
+
+  Urea stays close to pore center because it's hydrophilic
+  Acetamide stays a little closer to pore walls because it has hydrophobic character
+  That's why acetamide is slower
+  Acetic Acid is being slowed down by hydrogen bonding (compare to methanol)
+  Urea is slowed down by ..?
 
@@
   	\item Sulfur is unable to hydrogen bond, however it is soluble in water  %BJC: maybe a reference to why sulfur can't hbond
-  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
-  \end{itemize}
+ \end{itemize}
+
+%  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
+%  \end{itemize}
 
@@
 
-  \noindent Mercaptoethanol has a similar average RDF and MSD to ethylene glycol.
+  \noindent Mercaptoethanol has a similar average MSD and RDF to ethylene glycol.
   \begin{itemize}
@@
     is inherently slower, and may contribute to some slower MSDs.  % Can quantify as a percentage
-    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs  % Only methanol has greater (I think)
+    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs 
+    (See Figure~\ref{fig:SOH_trace})  % Only methanol has greater (I think)
     \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
@@
 
+  %BJC: Could be a supporting figure
   \begin{figure}
@@
     % BJC: can probably quantify the following:
-    \item It also hydrogen bonds with water molecules which increases its stability
+    \item It can also hydrogen bond with water molecules which increases its stability
     in the pore region.
@@
 
-  \noindent DMSO has a comparable MSD to acetone even though its molecular weight is
-  about 25 \% larger.
-  \begin{itemize}
+  \noindent DMSO has an average MSD nearly twice as large as acetone even though it
+  is a slightly larger molecule.
+  \begin{itemize}
+    \item The radial density of DMSO is higher than acetone close to the pore center.
   	\item The pyramidal structure of DMSO may force it to spend more time closer to
-  	the pore center.  % BJC: might be a good place for a numbers comparison
-  	\item There are 20 \% more acetone than DMSO molecules in the region beyond 
-  	0.8 nm from the pore center.  % based on actual number, not density
-  	\item DMSO cannot as easily work its way in and out of the dense head group region. % BJC: some kind of average regional lifetime
-  	\item There is a peak in DMSO's radial density near 1.1 nm which may be a consequence of 
-  	solute molecules that get stuck in the tails.
+  	the pore center.
   \end{itemize}
@@
 
-  The final set of molecules we studied can accept hydrogen bonds, but cannot donate
+  %BJC: should probably at least mention acetone again in this section  
+  The slowest set of molecules we studied can accept hydrogen bonds, but cannot donate
   them. 
@@
   	\item Among this set are the two slowest solutes in our study: Tetrahydrofuran and Dimethyl Formamide.
-  	\item Ethyl acetate and Propylene Carbonate are only marginally faster, however they
-  	are both larger molecules. %BJC: not sure how far I should dive into this point
+  	\item The MSDs of ethyl acetate and propylene carbonate are only marginally larger,
+  	however they are both larger molecules. %BJC: not sure how far I should dive into this point
   \end{itemize}
@@
   	% BJC:  Ethyl acetate spends all of its time in a linear or near-linear conformation.
-%  	\item The relatively small amount of movement on the timescales studied 
-%  	do not reveal definitive reasons
-  	\item Overall, 
+  \end{itemize}
+
+  The radial density of solutes near the pore center in this set is surprisingly high
+  as shown in Figure~\ref{fig:nondonors_rdf}.
+  \begin{itemize}
+    \item Propylene carbonate and ethyl acetate are among the largest solutes
+    in this study. Their size prevents them from easily entering the tail 
+    region and generally gives faster transport properties since they spend
+    more time in the pore region. 
+    \item However, this is not a hard rule. When a solute does overcome the 
+    barrier of entry beyond the head group region, it can become trapped. All
+    solutes in this set show a peak $geq$ 1 nm from the pore center which is
+    likely caused by solutes that get trapped in the tail region for a significant
+    amount of time.
+	\item The peak density of THF is considerably offset from the pore center.
+	\item Observations of single THF trajectories have revealed that it does not make
+	large hops while in the pore center.
+	\item THF becomes nearly immobilized while associated with sodium ions (See 
+	Figure~\ref{fig:thf_sodium_coordination}).
+	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
+	higher than THF near the head groups. The planar shape of DMF causes it to 
+	become stuck between head groups. Excursions into the pore region do not
+	necessarily result in large hops.
   \end{itemize}
@@
 
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
+  %BJC: figure was hard to make exactly how I wanted it so I stopped until we decide the best way to illustrate this point
+  %BJC: Should I do two colorbars (one for sodium, one for THF)
+  %BJC: Should Sodium-THF distance be between THF COM and sodium in order to be consistent with above figure? 
+  \caption{Coordination of THF with sodium ions may help stabilize it inside the
+  pore region. For the first 700 ns of the trajectories shown, the center of mass
+  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
+  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
+  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
+  After 700 ns, THF separates from the sodium ion and moves closer to the head group
+  region.}\label{fig:thf_sodium_coordination}
+  \end{figure}
+
   % THF shows highly anticorrelated hops
 
+  The majority of THF trajectories are spent near or beyond the head groups. Some
+  trajectories spend all of their time near the pore center but with very little movement. 
+  High densities in head group / tail region is a consequence of trajectories where THF
+  gets trapped there. Ring structure of THF makes it miscible with water (has dipole). Bulky alkyl
+  substituents are kept from interfering with oxygen's electron pairs. THF does not
+  make large hops in the pore center for some reason.
+  Water does not get close to THF when it's in the pore center
+  THF appears to prefer to associate with sodium 
+  THF is stabilized by sodium or by a hydrogen bond with water leaving oily groups alone which
+  don't want to move through the water. The effective size of THF increases and prevents it
+  from moving.
+
+  DMF shows similar characteristics, however spends a large proportion of its time trapped 
+  between head groups.
+
   %All have comparable densities near pore center except acetone which is lower
-
-  \subsection*{Transport of Ions} % probably just sodium
-
-  Sodium ions coordinate with water molecules.
-
-%  Sodium ions also exhibit hop diffusion because polarized water and
-%  carboxylate head groups both work to neutralize its charge.
-%  \begin{itemize}
-%	\item Ions get trapped in oxygen 'cages' composed of combinations
-%	of water molecules, carboxylate head groups and ether oxygens connecting
-%	the head groups to their tails.
-%  	\item Interesting coordination number data
-%	\item Dwell time proportional to surrounding charge within coordination shell
-%  \end{itemize}
 
@@
 
+  Two routes one might want to go down:
+  \begin{enumerate}
+    \item Only allow water to pass
+    \item Selective separation of a dissolved species.
+  \end{enumerate}
+
   Monomers that cannot hydrogen bond. % Hard to make a monomer like this
@@
   \end{itemize}
+
+  Ions with less water coordination (or more water) so that solutes can hbond with water
+  and perhaps be more inclined to stay in the pore region.
 

### 2019-03-02 Ben_Manuscripts/transport/figures/msd_bar_chart.py

@@ -5,12 +5,12 @@ import sqlite3 as sql
 import numpy as np
 import names
 
-connection = sql.connect("../../../timeseries/msd.db")
+connection = sql.connect("../../../LLC_Membranes/timeseries/msd.db")
 crsr = connection.cursor()
 restrict_by_name = False 
-MW = True  # plot mw of species
-penalty = 0.5
-wt = 5 
+MW = False  # plot mw of species
+penalty = 0.25
+wt = 10 
 
 group = 'all'
 
@@ -39,8 +39,9 @@ if restrict_by_name:
 	query += ') and'
 else:
 	query += ' WHERE'
-#query += " penalty = %s and" % penalty
+query += " penalty = %s and" % penalty
 query += " wt_water = %s" % wt
+query += " and name != 'HOH'"
 query += " ORDER BY MD_TAMSD DESC"
 
 output = crsr.execute(query).fetchall()
@@ -77,12 +78,13 @@ else:
 labels = labels[ordered_md]
 # end temporary block
 
-fig, ax = plt.subplots(figsize=(12, 7))
-bar_width = 0.4
+fig, ax = plt.subplots(figsize=(6, 7))
+bar_width = 0.8
 opacity = 0.8
 index = np.arange(len(labels), dtype=float)
+
 if not MW:
-	index += (bar_width / 2)
+	index += bar_width / 2
 
 if time_averaged:
 	ax.bar(index, md_tamsd, bar_width, alpha=opacity, yerr=(md_tamsd_lower, md_tamsd_upper), label='MD Simulated time-averaged MSD')
@@ -91,7 +93,7 @@ else:
 
 ax.set_ylabel('MSD ($nm^2$)', fontsize=14)
 ax.tick_params(labelsize=14)
-ax.set_xticks(index + bar_width/2)
+ax.set_xticks(index)# + bar_width/2)
 ax.set_xticklabels(labels, fontsize=14)
 plt.xticks(rotation=90)
 

### 2019-03-02 LLC_Membranes/analysis/msd.py

@@ -7,7 +7,7 @@ import numpy as np
 import mdtraj as md
 import matplotlib.pyplot as plt
 from LLC_Membranes.analysis import Poly_fit, top
-from LLC_Membranes.llclib import physical, topology, timeseries, fitting_functions, atom_props
+from LLC_Membranes.llclib import physical, topology, timeseries, fitting_functions, atom_props, file_rw
 from scipy import stats
 import tqdm
 import sqlite3 as sql
@@ -43,6 +43,8 @@ def initialize():
     parser.add_argument('--update', action="store_true", help="update database with MD MSD values")
     parser.add_argument('-wt', '--wt_water', default=10, type=float, help='Weight percent water in system. Only need'
                                                                           'to adjust this if updating database.')
+    parser.add_argument('-s', '--savename', default=False, type=str, help='If specified, save the MSD curve in a '
+                                                                          'pickled .pl file of this name.')
 
     return parser
 
@@ -78,7 +80,6 @@ class Diffusivity(object):
         print('Done!')
         self.nT = self.t.n_frames  # number of frames
         self.time = self.t.time / 1000  # time stamp on each frame, converted to nanoseconds
-        print(self.time[-1])
 
         # initialize fits to data, error analysis and plotting parameters
         self.startfit = int(startfit*self.nT)  # index at which to start fit
@@ -112,17 +113,15 @@ class Diffusivity(object):
             if res == 'SOL':  # mdtraj changes the name from SOL to HOH
                 res = 'HOH'
 
-            self.itp = "%s/%s.itp" % (self.top_location, res)
-
             if restrict:
                 selection = [a.index for a in self.t.topology.atoms if a.residue.name == res and a.index in restrict]
             else:
                 selection = [a.index for a in self.t.topology.atoms if a.residue.name == res]
 
-            topol = top.Top(self.itp)  # read topology
+            topol = topology.Residue(res)
             atoms_per_residue = topol.natoms  # number atoms in a single residue
-            matoms = topol.atom_masses  # mass of the atoms in residue
-            self.mres = np.sum(matoms)  # total mass of residue
[…]

### 2019-03-05 Ben_Manuscripts/transport/Outline.tex
fixing paths

@@
 
-  \noindent We measured the time-averaged mean squared displacement (MSD)
-  of the centers of mass of each solute over the course of 1 $\mu$s MD 
-  simulations using Equation~\ref{eqn:tamsd}.
+  \noindent We measured the time-averaged $z$-direction mean squared 
+  displacement (MSD) of the centers of mass of each solute over the 
+  course of 1 $\mu$s MD simulations using Equation~\ref{eqn:tamsd}.
   \begin{itemize}
@@
 
+  Using four different methods, Rowley and Roux observed peaks in the radial
+  distribution function for sodium coordinated with water at an O-Na distance 
+  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA as
+  the distance cutoff.
+
   \section{Results and Discussion}
 
-  \subsection*{Structure and Transport of Membrane Components}\label{section:membrane_components}
+  \subsection*{Structure and Transport of Membrane Constituents}\label{section:membrane_components}
 
@@
     \item Figure~\ref{fig:component_densities} plots the densities of each
-    membrane component.
+    membrane constituent.
     \item Water is densest at the center of each pore. 
-    \item Sodium ions are densest within the pore region, which we define as the
-    space between the pore center and the peak head group density.
+    \item Sodium ions are densest between the pore center and the peak head group density.
     \item The peak density of sodium ions is not at the pore center in either case
@@
 
-  The MSD of sodium and water become linear on long timescales.
-  \begin{itemize}
-    \item
-  \end{itemize}
+  The MSD of sodium and water is significantly larger in the 10 wt \% water system
+  versus the 5 wt \% water system.
+  \begin{itemize}
+    %BJC: these numbers will change. This is for incomplete methanol systems. I will
+    % redo calculations on pure water systems.
+    \item Water moves about 65 times faster and sodium moves about 40 times faster
+    in the 10 wt\% system.
+    \item Water moves about 65 times faster than sodium in the 10 wt \% system and
+    40 times faster than sodium in the 5 wt \% system. %BJC: weird coincidence
+    \item The diffusivity of water in the 10 wt \% system is still only 1 \% that of 
+    bulk water %BJC: 5.53e-07 versus 5.5e-05 cm^2/s
+  \end{itemize}
+
+  % BJC: could talk about subdiffusion a little here but I'd rather save it for 
+  % small molecule discussion
+
+%  \noindent The diffusion constant of water is about 50 times faster than sodium.
+%  \begin{itemize}
+%    \item In a dilute sodium chloride solution, the diffusivity of sodium
+%    is about 4 times slower than water.
+%    \item The carboxylate groups, whose oxygen atoms each have a charge of -0.822
+%    keep the positively charged sodium ions relatively close and restricts their
+%    motion.
+%  \end{itemize}
 
@@
   \end{subfigure}
-  \caption{}\label{fig:msd_comparison}
+  \caption{(a) The MSD of water in the 10 wt \% water system is about 65 times
+  higher than water in the 5 wt \% water system. (b) The MSD of sodium in the
+  10 wt \% water system is about 40 times higher than sodium in the 5 wt \% 
+  water system.}\label{fig:msd_comparison}
   \end{figure}
 
-  Sodium coordinates with water.
-
-  \noindent The diffusion constant of water is about 50 times faster than sodium.
-  \begin{itemize}
-    \item In a dilute sodium chloride solution, the diffusivity of sodium
-    is about 4 times slower than water.
-    \item The carboxylate groups, whose oxygen atoms each have a charge of -0.822
-    keep the positively charged sodium ions relatively close and restricts their
-    motion.
-  \end{itemize}
+  \noindent Sodium coordinates with water far less than in bulk solution.
+  \begin{itemize}
+    \item On average, each sodium ion is coordinated to about 1.7 water molecules in 
+    the 10 wt \% system and 1.15 water molecules in the 5 wt\% system.
+    \item In bulk water, it is estimated that sodium coordinates with 5.6 - 5.8 water
+    molecules~\cite{rowley_solvation_2012}
+    \item The low levels of water coordination under confinement are likely driven
+    in part by favorable interactions between sodium ions and carboxylate head groups.
+    \item A dehydrated sodium ion is not shielded from the negatively charged carboxylate
+    group.~\cite{ma_drastically_2019}
+  \end{itemize}
+
+  % BJC: This figure is from methanol simulations. Will be replaced by pure water
+  % simulations
+  % BJC: I can probably just report the averages rather than plot this
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
+  \caption{}\label{fig:na_water_coordination}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
+  \caption{}\label{fig:na_hg_coordination}
+  \end{subfigure}
+  \end{figure}
 
@@
 
-  \noindent The MSDs for the solutes studied in this work span a moderate range. 
-  \begin{itemize}
-    \item We plotted the 400 ns time-lag MSD for each solute in Figure~\ref{fig:all_msds}.
-  	\item The fastest solute, methanol, has an MSD over 20 times greater than
-  	the slowest, dimethyl formamide. 
-  \end{itemize}
-
-  \noindent The MSDs are not a monotonic function of solute size.
-  \begin{itemize}
-  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:all_msds}.
-  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
-  	than half of all solutes studied. 
-  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
-  	\item Transport is clearly affected by factors other than molecular size. 
-  \end{itemize}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.5\textwidth}
-  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}  % include bar plot of MW to show it's non-monotonic
-  \caption{}\label{fig:all_msds}
-  \end{subfigure}
-  \begin{subfigure}{0.5\textwidth}
-  \includegraphics[width=\textwidth]{msd_radius.pdf} 
-  \caption{}\label{fig:msd_radius}
-  \end{subfigure}
-  \caption{}\label{fig:msds}
-  \end{figure}
+  We observe trends in transport properties that are dependent on chemical 
+  environment within the nanopores as well as the chemical functionality of membrane
+  constituents rather than just solute size. 
+  \begin{itemize}
+    \item Polar solutes are slowed by interactions between monomer functional groups
+    and ions.
+    \item Solutes with hydrophobic character partition out of the pore and are 
+    slowed by densely packed organic monomer components.
+    \item A thorough understanding of these interactions will help us to create
+    monomer design principles.
+    \item We will begin our analysis by considering the collective trends observed  
+    across all systems and then focus on subsets of similar molecules where 
+    some exceptions occur. 
+  \end{itemize}
 
@@
 
+  Like water and sodium above, the MSDs of the solutes studied in this work are 
+  significantly larger in the 10 wt \% system, than those in the 5 wt \% water 
+  system (Figure~\ref{fig:msds}). 
+  \begin{itemize}
+    \item The fastest moving solute in both cases, methanol, has an MSD about 175
+    times larger in the 10 wt \% versus the 5 wt \% system.
+    \item Clearly the equilibrium water content of a given LLC system will 
+    determine its viability for real separations.
+  \end{itemize}
+
+%  \noindent The MSDs for the solutes studied in this work span a moderate range. 
+%  \begin{itemize}
+%    \item We plotted the 400 ns time-lag MSD for each solute in Figure~\ref{fig:all_msds}.
+%  	\item The fastest solute, methanol, has an MSD over 20 times greater than
+%  	the slowest, dimethyl formamide. 
+%  \end{itemize}
+
+  \noindent The MSDs are not a monotonic function of solute size.
+  \begin{itemize}
+  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
+  	\item There are numerous examples of solutes in our study that do not 
+  	follow the behavior set forth by the Stokes-Einstein equation which 
+  	implies that solute MSD should be inversely related to solute size.  % citation
+  	\item This behavior is not entirely surprising but worth emphasizing. 
+  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
+  	the solute radius is much larger than the solvent, should break down once
+  	solute and solvent are of comparable size.
+  	\item Membranes, including that studied here, are often characterized 
+  	with size-exclusion experiments which emphasizes selectivity based on the ability
+  	to enter a given pore. 
+  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
+  	becomes of secondary importance since the primary purpose of these membranes is to 
+  	separate molecules whose sizes are on the same order as water.
+  	\item In order to handle complex waste streams with molecules of similar size,
+  	it is important to take advantage of material properties other than pore size. 
+%  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
+%  	than half of all solutes studied. 
+%  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
+%  	\item Transport is clearly affected by factors other than molecular size. 
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
+  \caption{5 wt \% water}\label{fig:all_msds_5wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
+  \caption{10 wt \% water}\label{fig:all_msds_10wt}
+  \end{subfigure}
+  %BJC: missing a few since those simulations just got started
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
+  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
+  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
+  \end{subfigure}
+  \caption{}\label{fig:msds}
+  \end{figure}
+
   \noindent On the timescales simulated in our study, we observe subdiffusive behavior.
@@
     \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
-  	3 representative ethanol centers of mass.
+  	3 representative ethanol centers of mass in the 10 wt \% water system.
   	\item There are clear periods of entrapment separated by relatively large hops.
-	\item The MSD calculated based on all ethanol molecules is plotted in Figure~\ref{fig:example_msd}
-	and is sublinear.
+	\item The MSD calculated based on all ethanol molecules is plotted in 
+	Figure~\ref{fig:example_msd} and is sublinear.
 	\item The long periods of entrapment likely lead to this sublinear, and thus
@@
     \item It is clear from Figure~\ref{fig:example_ztraces} that the longest 
-    periods of entrapment generally occur when solutes are far from the pore
+    periods of entrapment usually occur when solutes are far from the pore
     center.
@@
     solutes are generally close to the pore center.
-    %BJC: need a radial density of head groups, tails, water etc.
     \item Solutes can move relatively freely when they enter the pore region
-    which is primarily composed of water molecules.
+    which is primarily composed of water molecules and sodium ions.
   \end{itemize}
@@
 
+  %BJC: need to check whether sodium ion association is exhibited by all solutes
   In addition to solute trapping in dense monomer regions, we observe a second
@@
     with water. 
-    \item This shows a high perference for the carboxylate anions since there
+    \item This shows a high preference for the carboxylate anions since there
     are 5 times more water molecules in the system.
@@
   \end{figure}
+
+  \noindent The transport behavior exhibited by solutes in the 5 wt \% water systems
+  is similar to those shown by those in the 10 wt \% system however the timescales are
+  much longer.
+  \begin{itemize}
+    %BJC: will put supporting data in supporting information
+    \item We observe subdiffusive behavior with intermittent hopping between
+    periods of entrapment.
+    \item The frequency and length of hops are both diminished in the 5 wt \% system.
+    \item Since there are only 24 solute molecules in each system, in order to obtain
+    better time-averaged descriptions of solute transport mechanisms, we will focus
+    the rest of our analysis on transport in the 10 wt \% water systems.
+  \end{itemize}
+
+  We will revisit our observations in the the context of specific groups of 
+  molecules in the discussion that follows.
 
@@
   % (b) Illustrate preference for hbonds carboxylate head groups
-
-  We will revisit our observations in the the context of specific groups of 
-  molecules in the discussion that follows.
 

### 2019-03-05 Ben_Manuscripts/transport/figures/msd_bar_chart.py

@@ -10,7 +10,7 @@ crsr = connection.cursor()
 restrict_by_name = False 
 MW = False  # plot mw of species
 penalty = 0.25
-wt = 10 
+wt = 5 
 
 group = 'all'
 
@@ -39,7 +39,10 @@ if restrict_by_name:
 	query += ') and'
 else:
 	query += ' WHERE'
-query += " penalty = %s and" % penalty
+
+if wt == 10:
+	query += " penalty = %s and" % penalty
+
 query += " wt_water = %s" % wt
 query += " and name != 'HOH'"
 query += " ORDER BY MD_TAMSD DESC"

### 2019-03-05 Ben_Manuscripts/transport/figures/msd_radius.py

@@ -7,6 +7,7 @@ import sqlite3 as sql
 path = "/home/bcoscia/PycharmProjects/LLC_Membranes/LLC_Membranes/analysis/"
 connection = sql.connect('%s/size.db' % path)
 crsr = connection.cursor()
+wt = 10 
 
 simple_alcohols = False 
 if simple_alcohols:
@@ -33,7 +34,10 @@ r_std = np.array([i[2] for i in radii])
 connection = sql.connect('%s/../timeseries/msd.db' % path)
 crsr = connection.cursor()
 
-command = "SELECT name, MD_TAMSD, MD_TAMSD_CI_lower, MD_TAMSD_CI_upper, sim_length FROM msd WHERE penalty = 0.25"
+command = "SELECT name, MD_TAMSD, MD_TAMSD_CI_lower, MD_TAMSD_CI_upper, sim_length FROM msd WHERE wt_water = %d and name != 'HOH'" % wt
+
+if wt == 10:
+	command += "and penalty = 0.25"
 
 if restrict:
 	command += ' and ('
@@ -71,7 +75,7 @@ plt.xticks(fontsize=14)
 plt.yticks(fontsize=14)
 plt.tight_layout()
 if restrict:
-	plt.savefig('msd_radius_simple_alcohols.pdf')
+	plt.savefig('msd_radius_simple_alcohols_%dwt.pdf' % wt)
 else:
-	plt.savefig('msd_radius.pdf')
+	plt.savefig('msd_radius_%dwt.pdf' % wt)
 plt.show()

### 2019-03-05 LLC_Membranes/BCC/Scripts/nsolvent.py

@@ -1,0 +1,37 @@
+#!/usr/bin/env python
+
+import argparse
+import bcc_class
+
+def initialize():
+
+    parser = argparse.ArgumentParser(description='Create bicontinuous cubic membrane structure')  # allow input from user
+
+    parser.add_argument('-b', '--build_mon', default='Dibrpyr14.gro', type=str, help='Name of monomer to build with')
+    parser.add_argument('-d', '--dim', default=10, type=float, help='Unit cell dimension (length of x, y and z vector)')
+    parser.add_argument('-dens', '--density', default=1.1, type=float, help='Density of system (g/cm3)')
+    parser.add_argument('-wt', '--weight_percent', default=77.1, type=float, help='Weight %% of monomer in membrane')
+    parser.add_argument('-sol', '--solvent', default='glycerol', type=str, help='Name of solvent mixed with monomer')
+
+    args = parser.parse_args()
+
+    return args
+
+if __name__ == "__main__":
+
+    args = initialize()
+
+    mw = {'glycerol': 92.09382}
+
+    LC = bcc_class.LC(args.build_mon)  # get all properties of the liquid crystal
+
+    # figure out how many solvent molecules are needed to achieve a certain weight percent
+    NA = 6.022 * 10 ** 23  # avogadros number
+    mass = LC.MW / NA  # mass of a single monomer (g)
+    V = args.dim ** 3 * 10 ** -21  # volume of unit cell (cm ^ 3)
+
+    mass = mw[args.solvent] / NA
+    solv_mass = args.density * V * (100 - args.weight_percent) / 100
+    nsol = int(solv_mass / mass)
+
+    print(nsol)

### 2019-03-05 LLC_Membranes/analysis/ztrace.py

@@ -79,7 +79,7 @@ class ZTrace(object):
 
             self.radial_distance[t, :] = d[np.argmin(d, axis=0), np.arange(self.nres)]
 
-    def plot_trace(self, nr, colormap='plasma_r', cmax=None, savename=None):
+    def plot_trace(self, nr, colormap='plasma_r', cmax=None, savename=None, show=True):
 
         fig, ax = plt.subplots()
 
@@ -128,7 +128,8 @@ class ZTrace(object):
         if savename is not None:
             plt.savefig(savename)
 
-        plt.show()
+        if show:
+            plt.show()
 
 
 if __name__ == "__main__":

### 2019-03-06 Ben_Manuscripts/transport/Outline.tex
Outline updates

@@
   of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA as
-  the distance cutoff.
+  the distance cutoff.  % BJC: this might be too strict. I've seen literature where they define 3.2 angstroms as the cutoff
 
@@
 
-  The MSD of sodium and water is significantly larger in the 10 wt \% water system
-  versus the 5 wt \% water system.
+%  The MSD of sodium and water is significantly larger in the 10 wt \% water system
+%  versus the 5 wt \% water system.
+  \noindent Water's mobility is increased when pores are larger and less crowded.
   \begin{itemize}
@@
     % redo calculations on pure water systems.
-    \item Water moves about 65 times faster and sodium moves about 40 times faster
-    in the 10 wt\% system.
+    \item The MSD of water is about 65 times higher and the MSD of sodium is about 40
+    times higher in the 10 wt\% system.
     \item Water moves about 65 times faster than sodium in the 10 wt \% system and
@@
 
-  \noindent Sodium coordinates with water far less than in bulk solution.
-  \begin{itemize}
-    \item On average, each sodium ion is coordinated to about 1.7 water molecules in 
-    the 10 wt \% system and 1.15 water molecules in the 5 wt\% system.
+  \noindent Sodium coordinates with far less water molecules than it does in 
+  bulk solution.
+  \begin{itemize}
     \item In bulk water, it is estimated that sodium coordinates with 5.6 - 5.8 water
     molecules~\cite{rowley_solvation_2012}
+    \item In our system, on average, each sodium ion is coordinated to about 1.7 
+    water molecules in the 10 wt \% system and 1.15 water molecules in the 5 wt\% 
+    system.
     \item The low levels of water coordination under confinement are likely driven
     in part by favorable interactions between sodium ions and carboxylate head groups.
-    \item A dehydrated sodium ion is not shielded from the negatively charged carboxylate
-    group.~\cite{ma_drastically_2019}
+    \item A dehydrated sodium ion is not shielded from the negatively charged 
+    carboxylate group.~\cite{ma_drastically_2019}
+    \item On average, sodium ions coordinate with 0.5 head group oxygen atoms in the
+    10 wt \% water system and 0.4 head group oxygen atoms in the 5 wt \% water system. 
+    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
+    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
+    % better to report average number of sodiums coordinated to a head group
   \end{itemize}
@@
   \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
-  \caption{}\label{fig:na_hg_coordination}
+  \caption{}\label{fig:na_hg_coordination}  % No caption since this probably won't be a figure
   \end{subfigure}
@@
   \end{subfigure}
-  \caption{}\label{fig:msds}
+  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
+  smaller than those of the solutes in the 10 wt \% water system (b). The
+  MSDs are not a monotonic function of molecular size (c and d).}\label{fig:msds}
   \end{figure}
 
-  \noindent On the timescales simulated in our study, we observe subdiffusive behavior.
+  \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
   %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
@@
 
-  Solutes partition out of the pore into the head group region and beyond which
+  \noindent Solutes partition out of the pore into the head group region and beyond which
   may lead to radially dependent transport mechanisms.
@@
     charge than water molecules.
-    \item Additionally, on average, each sodium ion is coordinated to 3 water
+    \item Additionally, on average, each sodium ion is coordinated to 1.7 water
     molecules. Roughly all of the water in the pore region is usually coordinated
@@
   \end{itemize}
+
+  Finally, we see instances of solutes which become immobilized or slowed by 
+  association with sodium counterions. 
+  \begin{itemize}
+    \item Much like water, the polarity of the solutes leaves partial negative
+    charges which are stabilized through electrostatic interactions with sodium ions.
+    \item There are many cases in which polar groups bind to sodium ions for at
+    least a few time steps. 
+    \item There are some cases where solutes become immobilized for long periods
+    of time while in close proximity to a sodium ion.
+    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
+    within 2.5 \AA of a sodium ion for the entire length of a trapping occurence.
+  \end{itemize}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}
+  \caption{The oxygen atom of methanol stays bound to the same sodium ion for
+  the majority of the trapping occurence between 400 and 600 ns. Regions
+  highlighted red or blue indicate times when methanol's oxygen atom is within 
+  2.5 \AA~of a sodium ion. The color of the shaded regions is switched every time
+  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
+  \end{figure}
 
@@
   	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
-  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Better word?
+  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Is there a better word?
   	\item The negative autocovariance at low values of k indicates anti-correlation
@@
 
-  We will revisit our observations in the the context of specific groups of 
-  molecules in the discussion that follows.
+%  We will revisit our observations in the the context of specific groups of 
+%  molecules in the discussion that follows.
 
@@
     \item The MSD of ethanol, propanol and butanol descend approximately
-    linearly as expected form the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
-    \item However, methanol travels considerably faster based on this relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
-  \end{itemize}
-
-  Methanol moves fast because it has the highest radial density near the pore center where
-  the largest hops occur.
+    linearly as expected from the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
+    \item However, methanol travels considerably faster than suggested by the
+    relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
+  \end{itemize}
+
+  Methanol moves fast, not only because it is the smallest solute studied in this work, but
+  because it has the highest radial density near the pore center where the largest hops occur.
   \begin{itemize}
@@
   \end{subfigure}
-  \caption{(a) The radial distribution functions of each simple alcohol shows a maximum close
+  \caption{(a) The MSD of the simple alcohols decrease as a function of the solute size, however
+  methanol's MSD is considerably higher than expected based on the Stokes-Einstein equation. 
+  (b) The radial distribution functions of each simple alcohol shows a maximum close
   to the highest density of monomer head groups (dashed line, normalized for easier visual
   comparison). Methanol spends the largest proportion of time, relative to the other alcohols,
-  near the pore center, which may help explain its fast dynamics. (b) Despite relatively little
+  near the pore center, which may help explain its fast dynamics. (c) Despite relatively little
   difference in the total number of hydrogen bond occurences, a given alcohol's preference
-  towards hydrogen bonds with the carboxylate groups increases with molecule size. (c) The average
+  towards hydrogen bonds with the carboxylate groups increases with molecule size. (d) The average
   location of butanol's oxygen atom is significantly closer to the pore center than its most distal
@@
     \item Somewhat counterintuitively, there is a relatively high density of ethylene
-    glycol molecules beyond the head group region. This likely contributes to the relatively
-    large error bars on its MSD in Figure~\ref{fig:all_msds}. 
+    glycol molecules beyond the head group region probably due to its relatively small size.
+    This likely contributes to the somewhat large error bars on its MSD in Figure~\ref{fig:msds}. 
     %BJC: can show figure of radial density colored with hop lengths
@@
 
-  The MSD of the solutes descend in order of their density close to the pore center.
+  \noindent The MSD of the solutes descend in order of their density close to the pore center.
   \begin{itemize}
     \item As shown in the radial density functions (Figure~\ref{fig:ketones_rdf}), 
-    Acetic has a fairly uniform and high density within the pore region.
+    Acetic acid has a fairly uniform and high density within the pore region.
     \item Acetone spends relatively little time near the pore center with its
@@
 
-  The amides, urea and acetamide hydrogen bond with head groups relatively infrequently.
-  \begin{itemize}
-    \item Acetic acid hydrogen bonds with head groups nearly 20 times as frequently.
+  \noindent The amides, urea and acetamide, hydrogen bond with head groups relatively 
+  infrequently, but regularly coordinate with sodium ions (See Figure~\ref{fig:ketones}).
+  \begin{itemize}
+    \item In an average frame, acetic acid participates in more than 12 hydrogen 
+    bonds with monomer head groups while urea and acetamide participate in less than 2.
     \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
   	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
-    \item The peaks in their radial density are closer to the pore center than 
-    other solutes that hydrogen bond with carboxylate groups (see 
-    Figure~\ref{fig:simple_alcohol_rdf} for example).
-  \end{itemize}
-
-  Urea stays close to pore center because it's hydrophilic
-  Acetamide stays a little closer to pore walls because it has hydrophobic character
-  That's why acetamide is slower
-  Acetic Acid is being slowed down by hydrogen bonding (compare to methanol)
-  Urea is slowed down by ..?
-
-  Once again, the trends in the MSD can in large part be explained by the solutes'
-  preference for water.
-  \begin{itemize}
-  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
-  	while acetone is the first instance of a molecule in this study that can only
-  	accept hydrogen bonds. It follows that acetone has the slowest MSD of this grouping.
-  	\item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
-  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
-  	\item Hence, Acetic Acid donates the greatest number of hydrogen bonds and has
-  	the highest density throughout the pore region.
-  	\item All other solutes show a higher preference for the tail region where three 
-  	dimensional confinement directly contributes to a lower MSD.
-  	\item Urea likely compensates for its loss of mobility in the head group region by
-  	making large hops upon escape into the pore region.
-  	\item Urea frequently moves between the head group and pore region because its planar
-  	shape makes it easier to transition between regions.% could quantify transition frequency probably. It seems like it might yield something. But also might make things more ambiguous.
-  	\item As the solutes become less polar, their MSD decreases. 
-  	\item Acetamide has one less amine group than Urea and a corresponding smaller MSD.
-  	\item Despite a peak in its density near the pore center due to its water solubility,
-  	Acetone is the least polar and spends the most time outside the tail group region 
-  	leading to the lowest MSD.
+  	\item Given their lower propensity to hydrogen bond one might expect amides to partition
+  	out of the pore and/or to move through the pore quickly, perhaps faster than methanol.
+    \item The peaks in their radial density are still situated between the pore center and the
+    head groups, but closer to the pore center than other solutes that hydrogen bond with 
+    carboxylate groups (see Figure~\ref{fig:simple_alcohol_rdf}, for example).
+    \item Both solutes spend about half of their time with their carbonyl oxygen atom 
+    coordinated to a sodium ion which restrains the solutes to within the pore region
+    %BJC: it's possible the solutes hop from sodium to sodium quickly meaning solutes are not always immobilized.
+    %BJC: could look into lifetime of association
+    \item Interestingly, the nitrogen atoms do not coordinate with any sodium ions despite
+    a similar negative partial charge. The hydrogen atoms may shield this interaction.
+  \end{itemize}
+
+  Acetone has the lowest MSD of this set because it is primarily trapped near and behind 
+  the head groups.
+  \begin{itemize}
+    \item On average, acetone coordinates with sodium with the same frequency as acetic acid 
+    \item However, acetic acid spends more time in the pore center and therefore encounters
+    more sodium ions.
+    \item When an acetone molecule coordinates with a sodium ion, its polarity is 
+    largely neutralized and it retreats towards the head group region where it can easily
+    get trapped.
+    \item Acetic acid and the amides and acetic acid have alternate hydrophlic
+    groups when bound to sodium ions which increases their stability in the pore.
+  \end{itemize}
+
+%  Once again, the trends in the MSD can in large part be explained by the solutes'
+%  preference for water.
+%  \begin{itemize}
+%  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
+%  	while acetone is the first instance of a molecule in this study that can only
+%  	accept hydrogen bonds. It follows that acetone has the slowest MSD of this grouping.
+%  	\item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
+%  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
+%  	\item Hence, Acetic Acid donates the greatest number of hydrogen bonds and has
+%  	the highest density throughout the pore region.
+%  	\item All other solutes show a higher preference for the tail region where three 
+%  	dimensional confinement directly contributes to a lower MSD.
+%  	\item Urea likely compensates for its loss of mobility in the head group region by
+%  	making large hops upon escape into the pore region.
+%  	\item Urea frequently moves between the head group and pore region because its planar
+%  	shape makes it easier to transition between regions.% could quantify transition frequency probably. It seems like it might yield something. But also might make things more ambiguous.
+%  	\item As the solutes become less polar, their MSD decreases. 
+%  	\item Acetamide has one less amine group than Urea and a corresponding smaller MSD.
+%  	\item Despite a peak in its density near the pore center due to its water solubility,
+%  	Acetone is the least polar and spends the most time outside the tail group region 
+%  	leading to the lowest MSD.
 %  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
@@
 %  	other is relatively deep in the head group region.
-  \end{itemize}
+%  \end{itemize}
 
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{ketone_ratio.pdf}
-  \caption{}\label{fig:ketones_ratio}
-  \end{subfigure}
+  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}
+  \caption{}\label{fig:ketone_hbonds}
+  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{ketone_ratio.pdf}
+%  \caption{}\label{fig:ketones_ratio}
+%  \end{subfigure}
+  \caption{(a) The radial density near the pore center (r = 0) decreases
+  with decreasing solute MSD. (b) The amides hydrogen bond with water far
+  less than acetic acid, however they tend to coordinate with sodium ions
+  more frequently.}\label{fig:ketones}
   \end{figure}
@@
     \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
-    \item It spends more time in the tail region than ethylene glycol, where transport
-    is inherently slower, and may contribute to some slower MSDs.  % Can quantify as a percentage
+    \item It spends more time in the tail region than
+    ethylene glycol, where transport is inherently slower, and may contribute to some
+    slower MSDs.  % Can quantify as a percentage
     \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs 
@@
   \end{subfigure}
-  \caption{}
+  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
+  to lengthy trapping. Large hops generally occur near the pore center while 
+  long entrapments occur while tangled among the monomer tails.}
   \end{figure}
@@
   \begin{itemize}
-    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
+    \item Glycerol frequently hydrogen bonds with more than one head group at a time (See Figure~\ref{fig:multi_hbonds}).
     % BJC: can probably quantify the following:
@@
 
-  \noindent DMSO has an average MSD nearly twice as large as acetone even though it
+  \noindent DMSO has a comparable if not large MSD than acetone even though it
   is a slightly larger molecule.
@@
   	the pore center.
+  	%BJC: quantify sodium coordination O group of DMSO
   \end{itemize}
@@
   	\item Among this set are the two slowest solutes in our study: Tetrahydrofuran and Dimethyl Formamide.
-  	\item The MSDs of ethyl acetate and propylene carbonate are only marginally larger,
-  	however they are both larger molecules. %BJC: not sure how far I should dive into this point
-  \end{itemize}
-
-  The radial density functions highlight the solutes' preference for the 
-  head group region.
-  \begin{itemize}
-  	\item There are small peaks in the radial density greater than 1 nm 
-  	from the pore center.
-  	\item The solutes become trapped in these regions where each step is
-  	highly anti-correlated to its previous step, leading to very low MSDs.
-  	\item The large size and nonplanar shapes of ethyl acetate and propylene 
-  	carbonate may destabilize entrapment in the tail region more quickly, leading
-  	to slightly faster transport. 
-  	% BJC:  Ethyl acetate spends all of its time in a linear or near-linear conformation.
-  \end{itemize}
+  	\item The MSDs of ethyl acetate, propylene carbonate and acetone are only marginally larger.
+  	% EAC and PCB are both larger molecules. Acetone is small. %BJC: not sure how far I should dive into this point
+  \end{itemize}
+
+%  The radial density functions highlight the solutes' preference for the 
+%  head group region.
+%  \begin{itemize}
+%  	\item There are small peaks in the radial density greater than 1 nm 
+%  	from the pore center.
+%  	\item The solutes become trapped in these regions where each step is
+%  	highly anti-correlated to its previous step, leading to very low MSDs.
+%  	\item The large size and nonplanar shapes of ethyl acetate and propylene 
+%  	carbonate may destabilize entrapment in the tail region more quickly, leading
+%  	to slightly faster transport. 
+%  	% BJC:  Ethyl acetate spends all of its time in a linear or near-linear conformation.
+%  \end{itemize}
 
@@
 
+  Carbonyl groups continue to show high degrees of association with sodium ions. 
+  \begin{itemize}
+    \item The number of sodium ions coordinated to the carbonyl group of 
+    propylene carbonate, dimethyl formamide, ethyl acetate are consistent with 
+    that shown by acetone, all between 6 and 7 per frame (See 
+    figure~\ref{fig:nondonors_hbonds})
+    \item The carbonyl group of the amides studied in the previous section
+    associate with sodium nearly twice as frequently as compounds that don't
+    contain nitrogen (see figure~\ref{fig:ketone_hbonds}).
+    \item In all cases, other polar groups on carbonyl-containing compounds
+    associate with sodium in negligible amounts.
+  \end{itemize}
+
   \begin{figure}
   \centering
-  \includegraphics[width=0.45\textwidth]{nondonors_rdf.pdf}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{nondonors_rdf.pdf}
   \caption{}\label{fig:nondonors_rdf}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{nondonor_hbonds.pdf}
+  \caption{}\label{fig:nondonors_hbonds}
+  \end{subfigure}
   \end{figure}
@@
 
-  The majority of THF trajectories are spent near or beyond the head groups. Some
-  trajectories spend all of their time near the pore center but with very little movement. 
-  High densities in head group / tail region is a consequence of trajectories where THF
-  gets trapped there. Ring structure of THF makes it miscible with water (has dipole). Bulky alkyl
-  substituents are kept from interfering with oxygen's electron pairs. THF does not
-  make large hops in the pore center for some reason.
-  Water does not get close to THF when it's in the pore center
-  THF appears to prefer to associate with sodium 
-  THF is stabilized by sodium or by a hydrogen bond with water leaving oily groups alone which
-  don't want to move through the water. The effective size of THF increases and prevents it
-  from moving.
-
-  DMF shows similar characteristics, however spends a large proportion of its time trapped 
-  between head groups.
+%  The majority of THF trajectories are spent near or beyond the head groups. Some
+%  trajectories spend all of their time near the pore center but with very little movement. 
+%  High densities in head group / tail region is a consequence of trajectories where THF
+%  gets trapped there. Ring structure of THF makes it miscible with water (has dipole). Bulky alkyl
+%  substituents are kept from interfering with oxygen's electron pairs. THF does not
+%  make large hops in the pore center for some reason.
+%  Water does not get close to THF when it's in the pore center
+%  THF appears to prefer to associate with sodium 
+%  THF is stabilized by sodium or by a hydrogen bond with water leaving oily groups alone which
+%  don't want to move through the water. The effective size of THF increases and prevents it
+%  from moving.
+%  
+%  DMF shows similar characteristics, however spends a large proportion of its time trapped 
+%  between head groups.
 

### 2019-03-08 Ben_Manuscripts/transport/Outline.tex
Updated documentation and outline

@@
 %\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
-\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+%\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Chemically Dependent Selectivity in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
 
+  Python scripts used to set up systems and conduct post-simulation trajectory analysis are
+  available online at \texttt{https://github.com/bencoscia/llcsim}.
+
+  \noindent We ran all molecular dynamics simulations and energy minimizations using 
+  GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
+
   \subsection*{System Setup}
@@
 	\item See supporting info for water equilibration simulation data.
-	\item We adjusted the pore radius in our systems so that the right amount of water
-	fits in the pores without any vacuum using \texttt{gmx solvate}.
+	\item We iteratively adjusted the pore radius in our systems until the right amount of water
+	fit in the pores when we ran \texttt{gmx solvate}.
 	\item We placed water molecules in the tail region one at a time in random locations
@@
   \begin{itemize}
-	\item We equilibrated the initial configuration using the `wet'
+	\item First, we equilibrated the initial configuration using the `wet'
 	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
-	\item We cross-linked the equilibrated solvated configuration using the
+	\item Then we cross-linked the equilibrated solvated configuration using the
 	cross-linking procedure described in our previous work. 
@@
 	pressure control
-	\item We collected transport data using 1 $\mu$s simulations
-  \end{itemize}
+	\item We collected transport data over the course of 1 $\mu$s MD simulations
+  \end{itemize}
+
+  \subsection*{Solute Parameterization}
+
+  %BJC: might need to reword. Most of this is taken from my last paper and adapted to solutes.
+  Like we have previously done for Na-GA3C11~\cite{coscia_understanding_2019}, we
+  parameterized the interaction potential for the solutes using the Generalized 
+  AMBER Force Field (GAFF)~\cite{wang_development_2004} with the Antechamber package
+  \cite{wang_automatic_2006} provided with AmberTools16~\cite{case_ambertools16_2016}.
+  We chose GAFF because it has been parameterized for use with organic molecules. We
+  assigned atomic charges using the am1bccsym method of \texttt{molcharge} shipped
+  with QUACPAC from Openeye Scientific Software.
 
@@
   \begin{itemize}
-	\item Ageing is defined by the tendency of the average MSD to decrease
+	\item Ageing is defined by the tendency of the average slope of an MSD curve to decrease
 	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
@@
 	\item As measurement time or trajectory length is increased, longer dwell times
-	are incorporated into the calculation, lowering the average MSD. (See supporting
-	info for demonstration)
+	are incorporated into the calculation, lowering the average MSD.
 	\item Because the MSDs are non-linear and because of the ageing phenomenon, we
@@
 	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
-	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
-	function, cost function penalty	tolerance, number of dimensions used)
+%	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
+%	function, cost function penalty	tolerance, number of dimensions used)
 	\item The corresponding hop lengths and dwell times between break points were 
@@
   distribution function for sodium coordinated with water at an O-Na distance 
-  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA as
+  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA~as
   the distance cutoff.  % BJC: this might be too strict. I've seen literature where they define 3.2 angstroms as the cutoff
@@
   near the pore center, which may help explain its fast dynamics. (c) Despite relatively little
-  difference in the total number of hydrogen bond occurences, a given alcohol's preference
+  difference in the total number of active hydrogen bonds per frame, a given alcohol's preference
   towards hydrogen bonds with the carboxylate groups increases with molecule size. (d) The average
@@
   \end{subfigure}
-  \caption{The number of hydrogen bond interactions between solutes and monomers increases
-  as solutes gain additional hydroxyl groups. Multiple hydroxyl groups within a solute often
-  hydrogen bond in different locations simultaneously. Occasionally, all four hydroxyl groups
+  \caption{(a) Glycerol, tetrose and ribose are densest close to the pore center because
+  they have a high number of hydrophilic groups and are relatively large. Ethylene glycol
+  and propylene glycol are densest close to the head group region. (b)The number of 
+  hydrogen bond interactions between solutes and monomers increases as solutes gain additional
+  hydroxyl groups. Often, multiple hydroxyl groups within a solute often hydrogen bond in
+  different locations simultaneously. Occasionally, all four hydroxyl groups
   of Ribose (n = 4) are involved in a hydrogen bond interaction at the same time.}\label{fig:multi_hbonds}
@@
     %BJC: could look into lifetime of association
-    \item Interestingly, the nitrogen atoms do not coordinate with any sodium ions despite
-    a similar negative partial charge. The hydrogen atoms may shield this interaction.
-  \end{itemize}
-
-  Acetone has the lowest MSD of this set because it is primarily trapped near and behind 
+    \item Interestingly, only the carbonyl oxygen atoms coordinate with sodium ions. 
+    The nitrogen atoms dooes not coordinate at all despite a similar negative partial
+    charge. The attached hydrogen atoms may shield this interaction.
+  \end{itemize}
+
+  \noindent Acetone has the lowest MSD of this set because it is primarily trapped near and behind 
   the head groups.
@@
     get trapped.
-    \item Acetic acid and the amides and acetic acid have alternate hydrophlic
-    groups when bound to sodium ions which increases their stability in the pore.
+    \item Acetic acid and the amides have other, unoccupied, hydrophilic groups while bound
+    to sodium ions which increases their stability in the pore.
   \end{itemize}
@@
   \end{subfigure}
-  \caption{}\label{fig:sulfur_analog_rdfs}
+  \caption{(a) The RDF of mercaptoethanol is similar to ethylene glycol except 
+  for its higher density in the tail region. (b) 2,3-Dimercapto-1-propanol is
+  densest near the pore wall, unlike glycerol whose density is very high in the pore
+  center. (c) Dimethylsulfoxide has a higher density than acetone close to the pore
+  center which may in part explain its marginally larger MSD.}\label{fig:sulfur_analog_rdfs}
   \end{figure}
@@
     \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
-    \item It spends more time in the tail region than
-    ethylene glycol, where transport is inherently slower, and may contribute to some
-    slower MSDs.  % Can quantify as a percentage
-    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs 
+    \item Some of this can be accounted for by the higher density of mercaptoethanol 
+    molecules in the head group / tail region, where transport is inherently slower. 
+    \item There are nearly 40 \% more mercaptoethanol molecules than ethylene 
+    glycol molecules beyond 0.8 nm from the pore center. 
+    \item Conversely, mercaptoethanol exhibits some of the highest single solute MSDs 
     (See Figure~\ref{fig:SOH_trace})  % Only methanol has greater (I think)
@@
     \item This may lead to larger hops in the pore region.
-    \item Some of this can be accounted for by the higher density of mercaptoethanol 
-    molecules in the head group / tail region. There are nearly 40 \% more mercaptoethanol
-    molecules than ethylene glycol molecules beyond 0.8 nm from the pore center. 
 %    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
@@
 
-  \noindent DMSO has a comparable if not large MSD than acetone even though it
+  \noindent DMSO has a comparable if not larger MSD than acetone even though it
   is a slightly larger molecule.
@@
 
-  The radial density of solutes near the pore center in this set is surprisingly high
+  \noindent The radial density of solutes near the pore center in this set is surprisingly high
   as shown in Figure~\ref{fig:nondonors_rdf}.
@@
     barrier of entry beyond the head group region, it can become trapped. All
-    solutes in this set show a peak $geq$ 1 nm from the pore center which is
+    solutes in this set show a peak $\geq$ 1 nm from the pore center which is
     likely caused by solutes that get trapped in the tail region for a significant
@@
 
-  Carbonyl groups continue to show high degrees of association with sodium ions. 
+  \noindent Carbonyl groups continue to show high degrees of association with sodium ions. 
   \begin{itemize}
@@
 
-  \subsection{Design Principles}
-
-  Water content affects pore size and strongly influence the MSD of both solutes and
-  water. Experiments to understand how controllable this parameter is could be useful.
-
-  Two routes one might want to go down:
-  \begin{enumerate}
-    \item Only allow water to pass
-    \item Selective separation of a dissolved species.
-  \end{enumerate}
-
-  Monomers that cannot hydrogen bond. % Hard to make a monomer like this
-
-  Separate polar molecules by creating monomers with head group components designed to
-  hydrogen bond.
-  \begin{itemize}
-  	\item Hbond donors
-	\item More incentive to dwell on walls.
-  \end{itemize}
-
-  Ions with less water coordination (or more water) so that solutes can hbond with water
-  and perhaps be more inclined to stay in the pore region.
+  \subsection{Design Considerations}
+
+  Based on our observations of the complex interactions between various polar solutes
+  and the membrane's liquid crystal monomers, we can speculate on design criteria for 
+  the next generation of liquid crystal monomers to be used for LLC membrane
+  synthesis.
+  \begin{itemize}
+    \item Unfortunately, we cannot comment on the stability of the H\textsubscript{II}
+    phase if major changes are made to the monomers.
+    \item Therefore, our most feasible design suggestions are those which can be made
+    as a post-processing step to the cross-linked membrane created using Na-GA3C11.
+  \end{itemize}
+
+  The transport properties of solutes are a strong function of the 3 trapping
+  mechanisms discussed above. Therefore, it is most logical to design monomers with 
+  them in mind.
+
+  Since solutes move slowly well entangled among the monomer tails, one can try to
+  design monomers that better control the partition of solutes between the pore and
+  tail region.
+  \begin{itemize}
+    \item The head groups of Na-GA3C11 are planar which leaves a fair amount of space
+    between adjacent head groups and it makes it easier for solutes to slip between and
+    past them.
+    \item Bulkier substituents, which do not impede stacking of monomers into columns,
+    might slow the rate at which solutes partition into the tails.
+    \item Additionally, one can include crosslinkable groups near the head groups in
+    order to fill free volume and effectively create a wall.
+    \item Finally, removal of the ether linkages between the head groups and the monomer
+    tails will decrease the stability of polar molecules in the head group region.
+    \item Overall, controlling the solute partition might not be the most important 
+    consideration to optimize because once enough solutes flow through, the membrane tail
+    region will become saturated with solute molecules and greatly reduce the rate of partition.
+  \end{itemize}
+
+  Alternatively, one can focus on designing head groups with varying hydrogen 
+  bonding capabilites.
+  \begin{itemize}
+    \item Na-GA3C11 has a carboxylate group which readily accepts hydrogen bonds
+    \item One can increase the number of hydrogen bonding sites on the head groups
+    in order to trap more solutes, or decrease the number of hydrogen bond sites
+    to trap less.
+  \end{itemize}
+
+  Finally, one can attempt to control the degree to which solutes coordinate 
+  with counterions.
+  \begin{itemize}
+    \item We have observed a significant amount of sodium association with 
+    negatively charge solute constituents.
+    \item Changing the size and valence of the counter ion may offer some
+    interesting behavior. 
+    \item For example, a counter ion with a charge of +2 may attract more solute
+    molecules and bind them more tightly, but there will only be half as many
+    counterions in the system which may reduce its overall influence.
+    \item Additionally, the size of the counterion will affect the mobility
+    of any complex formed. 
+    \item Sodium appears to do a good job of immobilizing complexes formed between
+    it and solutes. 
+    \item However, a Lithium ion might be more prone to go along for the ride.
+    \item Hydrogen would likely spend the majority of its time bound to the 
+    carboxylate head group or as part of a hydronium ion hence interfering with 
+    solute transport infrequently.
+  \end{itemize}
+
+%  There are two types of separations for which this membrane may have some use.
+%  \begin{enumerate}
+%    \item In a purification process, one may only desire water to pass. In this 
+%    case, water should have much faster dynamics than any other dissolved species.~\label{sep:purification}
+%    \item For a separate application, one may desire to selectively separate a 
+%    dissolved species from a complex stream.~\label{sep:selective}
+%  \end{enumerate}
+
+  The MSD of solutes may be much larger in more concentrated solutions because there
+  will be less available trapping sites for them to occupy.
+  \begin{itemize}
+    \item We purposely studied the behavior of the solutes in dilute conditions.
+    \item The difference in size between water and the fastest solute, methanol, is not
+    enough to explain the order of magnitude difference in their average MSDs.
+    \item The sheer number of water molecules prevents the majority of them from 
+    becoming trapped for long periods of time.
+    \item A similar effect may increase solute MSDs in more concentrated solutions.
+  \end{itemize}
+
+  As a final consideration, water content affects pore size and strongly influences
+  the MSDs of solutes, water and counterions.
+  \begin{itemize}
+    \item The MSD of these components is about 2 orders of magnitude larger in the 
+    10 wt \% system than the 5 wt \% system.
+    \item The 5 wt \% system is much less feasible as a separations membrane on the basis
+    of water permeability alone.
+    \item Typically, the total water content used to create the H\textsubscript{II} phase
+    is reported, but the amount of water that resides in the pores, tails and in between
+    hexagonal mesophases is less clear.
+    \item Experiments, such as those by Jenkins et al.~\cite{jenkins_identification_2012}, 
+    may help elucidate the water composition in each region.
+    \item The results would be extremely useful for determining the viability of a given
+    LLC membrane system. 
+  \end{itemize}
 
@@
   We have examined the transport characteristics of a series of small polar
-  molecules in our model of the H\textsubscript{II} phase formed by 
-  Na-GA3C11.
-
-  We calculated the macroscopic diffusion coefficients of each solute as 
-  approximated by a CTRW model and validated our estimates using experimental
-  DOSY NMR measurements.
-
-  We have studied the influence of water content on the diffusion coefficients.
-
-  We showed that hydrogen bonding between solutes and Na-GA3C11 monomers plays
-  a major role in mechanism by which molecules traverse the nanopores.
-
-  We can use this intuition in order to modify our monomers for a specific 
-  separation.
-  \begin{itemize}
-	\item Increase number of h-bond sites to increase selectivity towards water 
-	over polar molecules
-  \end{itemize}
+  molecules in our model of the H\textsubscript{II} phase formed by the liquid 
+  crystal monomer Na-GA3C11.
+
+  We learned that the MSD of solutes, water and counter ions are highly dependent 
+  on LLC membrane water content.
+  \begin{itemize}
+    \item As more water is added to the system, the pores become less crowded
+    with monomer components and the MSD of water, sodium and solutes increase.
+    \item The amount of water in the pores deserves special attention when 
+    screening new monomers.
+  \end{itemize}
+
+  We learned that solutes undergo anomalous diffusion which can be described 
+  as a subordinated fractional brownian motion process. 
+  \begin{itemize}
+    \item In general, solutes hop intermittently between periods of entrapment
+    \item These hops are anti-correlated to their previous hops
+  \end{itemize}
+
+  We observed three mechanisms of solute entrapment.
+  \begin{itemize}
+    \item A solute can become stuck in the tail region. 
+    \item A solute can hydrogen bond with monomers
+    \item A solute can associate with a bound counterion
+  \end{itemize}
+
+  Based on these trapping mechanisms, we have suggested modifications that
+  can be made to monomers in order to mitigate or enhance their effect on
+  solute MSDs.
 

### 2019-03-13 Ben_Manuscripts/transport/Supporting_Information.tex
updates

@@
   \bibliographystyle{ieeetr}
+
+  \section{Setup and analysis scripts}\label{section:python_scripts}
+
+  All python and bash scripts used to set up systems and conduct post-simulation trajectory
+  analysis are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
+  Documentation for the \texttt{LLC\_Membranes} repository is available at 
+  \texttt{https://llc-membranes.readthedocs.io/en/latest/}. Table~\ref{table:python_scripts}
+  provides more detail about specific scripts used for each type of analysis performed in
+  the main text.
+
+  \begin{table}[htb!]
+  \centering
+  \newcolumntype{A}{ >{\centering\arraybackslash} m{2.5in} }
+  \newcolumntype{B}{ >{\centering\arraybackslash} m{0.75in} }
+  \newcolumntype{C}{m{2.75in}}
+  \begin{tabular}{|A|B|C|}
+  \hline
+  \textbf{Script Name} & \textbf{Section} & ~~~~~~~~~~~~~~~~~~~~~\textbf{Description} \\
+  \hline
+
+  \texttt{/setup/param.sh} & TBD & Parameterize liquid crystal monomers and 
+  solutes with GAFF \\ \hline
+
+  \texttt{/setup/solvation\_equilibration.py} & TBD & Add water to the pores and tails
+  in order to achieve a specific total water content and ratio of water molecules in each
+  region, then equilibrate the solvated system. \\ \hline
+
+  \texttt{/setup/input.py} & TBD & Create GROMACS topology and .mdp files \\ \hline
+
+  \texttt{/setup/xlink.py} & TBD & Iteratively cross-link a configuration \\ \hline
+
+  \texttt{/setup/place\_solutes\_pores.py} & TBD & Place a desired number of solutes
+  in the pore center, equally space in the $z$-direction. \\ \hline
+
+  \texttt{/analysis/msd.py} & TBD & Calculate the mean squared displacement of residues \\ \hline
+
+  \texttt{/analysis/rdf.py} & TBD & Calculate the cylindrical radial distribution function of
+  a solute or membrane component with respect to the pore centers. \\ \hline
+
+  \texttt{/analysis/hbonds.py} & TBD & Identify hydrogen bonds based on geometric criteria \\ \hline
+
+  \texttt{/timeseries/forecast\_ctrw.py} & TBD & Construct dwell time and hop length distributions \\ \hline
+
+  \texttt{/analysis/coordination\_number.py} & TBD & Calculate number of molecules or atoms within a
+  cutoff distance of another type of molecule or atom. \\ \hline
+
+  \texttt{/analysis/ztrace.py} & TBD & Plot the center of mass $z$-coordinate of an atom or molecule
+  versus time which is colored according to its distance from the pore center. \\ \hline
+
+  \end{tabular}
+
+  \caption{The first column provides the names of the python scripts available in
+  the \texttt{LLC\_Membranes} GitHub repository that were used for system setup and 
+  post-simulation trajectory analysis. Paths preceding script names are relative to the
+  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second columns lists the section in the main
+  text where the output or usage of the script is first described. The third column
+  gives a brief description of the purpose of each script.
+  }~\label{table:python_scripts}
+
+  \end{table}
 
@@
   \includegraphics[width=\linewidth]{r5_gap.pdf}
-  \caption{r = 5\AA}\label{fig:r5_gap}
+  \caption{r = 5~\AA}\label{fig:r5_gap}
   \end{subfigure}
@@
   \includegraphics[width=\linewidth]{r6_gap.pdf}
-  \caption{r = 6\AA}\label{fig:r6_gap}
+  \caption{r = 6~\AA}\label{fig:r6_gap}
   \end{subfigure}
@@
   \includegraphics[width=\linewidth]{r7_gap.pdf}
-  \caption{r = 7\AA}\label{fig:r7_gap}
+  \caption{r = 7~\AA}\label{fig:r7_gap}
   \end{subfigure}
@@
   \includegraphics[width=\linewidth]{r8_gap.pdf}
-  \caption{r = 8\AA}\label{fig:r8_gap}
+  \caption{r = 8~\AA}\label{fig:r8_gap}
   \end{subfigure}
-  \caption{}\label{fig:gap_prefilled_equil}
+  \caption{There is likely more water in the pore region than in the tail region.
+  When we create configurations with more water in the tails, equilibration is 
+  slow. When configurations start with more water in the pores, the water content
+  in each region equilibrates quickly.}\label{fig:gap_prefilled_equil}
   \end{figure}
@@
   Figure~\ref{fig:gap_prefilled_equil}. We considered the water content
-  equilibrated once the water contents plateaued. The 10 wt \% water system
-  equilibrated within the first 100 ns of simulation, while the 5 wt\% system did
-  not plateau until $\sim$ 600 ns (See Figure~\ref{fig:solvation_equilibration}).
+  equilibrated once the water contents plateaued. The 5 wt\% system did
+  not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
+  while the 10 wt \% water system equilibrated within the first 100 ns of 
+  simulation (Figure~\ref{fig:10wt_offset_equil}).
   The pores contain 72 \% and 69 \% of the total water in the 5 and 10 wt \%
@@
   \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
-  \caption{}\label{fig:5wt_offset_equil}
+  \caption{5 wt \%}\label{fig:5wt_offset_equil}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
-  \caption{}\label{fig:10wt_offset_equil}
+  \caption{10 wt \%}\label{fig:10wt_offset_equil}
 % Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
@@
 	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
-	  ns, with $\sim$ 69 \% the total water in the
+	  ns, with $\sim$ 69 \% of the total water in the
 	  pores.}\label{fig:solvation_equilibration}
@@
   We cross-linked the equilibrated solvated systems, then allowed them to 
-  equilibrate further for 100 ns.
+  equilibrate further for 100 ns. The water contents in each region does not
+  change significantly in either case.
 
@@
   \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
-  \caption{}\label{fig:5wt_offset_xlinked_equil}
+  \caption{5 wt\%}\label{fig:5wt_offset_xlinked_equil}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
-  \caption{}\label{fig:10wt_offset_xlinked_equil}
+  \caption{10 wt\%}\label{fig:10wt_offset_xlinked_equil}
 % Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
@@
   \end{subfigure}
-  \caption{}\label{fig:solvation_equilibration}
+  \caption{The water content in the tail and pore region is not affected
+  by cross-linking}\label{fig:solvation_equilibration}
   \end{figure}
 
-  \section{Choosing a transport model}\label{section:transport_model_selection}
+  \subsection{Solute Interaction}\label{section:solute_interaction}
 
-  We used the toolbox created by Meroz and Sokolov in order to justify our
-  choice of transport model.\cite{meroz_toolbox_2015} The solutes in our systems
-  exhibit anomalous transport properties characteristic of a Continuous Time
-  Random Walk (CTRW).
+  We chose to model 6 solutes in each pore because there was a low degree of 
+  interaction between solutes which gave us a sufficient number of independent 
+  trajectories to observe and analyze. There are a negligible number of occurences
+  % BJC: not sure what the appropriate cut-off should be
+  where the center of a given solute came within 3.5 \AA of another same-solute
+  center of mass.
 
-  \subsection*{Mean Squared Displacement}
-
-  The general form of a mean squared displacement (MSD) curve is:
-  \begin{equation}
-	\langle x^2(t) \rangle \sim t ^ \alpha
-	\label{eqn:msd}
-  \end{equation}
-  For brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq
-  1$, the particle of interest exhibits anomalous diffusion. Values of $\alpha$
-  greater than 1 give rise to superdiffusion, while values of $\alpha$ less than
-  1 give rise to subdiffusion.
-
-  We can calculate the ensemble-averaged MSD curve by averaging the MSDs of
-  each particle trajectory, where each MSD is calculated using:
-  \begin{equation}
-	\delta^2(t) = \| \mathbf{r}(t) - \mathbf{r}(0) \|^2
-	\label{eqn:ensemble_msd}
-  \end{equation}
-  where $\|\cdot\|$ represents the Euclidean norm.
-
-  The mean squared displacement of solutes in our model is a non-linear
-  function of time, with $\alpha < 1$ which is indicative of anomalous
-  subdiffusion. Figure \ref{fig:msd_power_law}a plots the ensemble-averaged MSD
-  curve for 24 ethanol molecules diffusing in a 10 wt\% water H\textsubscript{II}
-  LLC membrane system. We fit a power law of the form $Ae^{\alpha}$ to the MSD
-  curve. We performed 2000 bootstrap trials by randomly sampling 24 MSD curves
-  with replacement from the 24 total ethanol MSD curves. The bootstrapped average
-  value of $\alpha$ is 0.75 for this system.
-
-  \begin{figure}[!htb]
+  \begin{figure}
   \centering
-% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -ensemble -power_law -a z -nboot 2000
-% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
-  \includegraphics[width=0.8\linewidth]{msd_power_law.pdf}
-  \caption{(a) We fit a curve with the form of Equation~\ref{eqn:msd} to the
-	  ensemble-averaged MSD curve. (b) The average value of $\alpha$, obtained using
-	  fits to MSDs calculated from bootstrapped ensembles, is less than 1 suggesting
-	  that ethanol molecules in our model exhibit subdiffusive
-	  behavior.}\label{fig:msd_power_law}
+  \includegraphics[width=0.45\textwidth]{solute_interaction.pdf}
+  \caption{Interactions between same-solutes are negligible when systems are 
+  built with 6 solutes per pore. Even methanol, which interacts with other same-solute
+  molcules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interation}
   \end{figure}
 
-  \subsection*{Ergodicity}
-
-  The ergodicity of a system can help us narrow down the possible anomalous
-  diffusion mechanisms. In an ergodic system, the time-averaged behavior of an
-  observable should yield the same result as the ensemble average of the same
-  observable. Examples of anomalous diffusion processes that are ergodic include
-  random walks on fractals (RWF) and fractional brownian motion (FBM).
-  Non-ergodic systems generally give rise to CTRWs with the possibility of
-  combination with a RWF and/or FBM.\cite{meroz_toolbox_2015}
-
-  We tested the ergodicity of our system by comparing the ensemble-averaged
-  and time-averaged MSD curves. We calculated the MSD of each ethanol trajectory
-  using Equation~\ref{eqn:ensemble_msd} and a time-averaged algorithm: 
-  \begin{equation}
-	\delta^2(t) = \dfrac{1}{N-t} \sum_{i=0}^{N-t-1} \| \mathbf{r}(i + t) - \mathbf{r}(i) \|^2
-  \end{equation}
-  where N is the total number of simulation frames, and t represents the length
-  of subinterval or number of frames per subinterval. We averaged the MSD curves
-  from each trajectory in order to create final MSD plots.
-
-  The ethanol molecules exhibit non-ergodic behavior because their
-  time-averaged and ensemble-averaged MSDs do not agree with each other
-  (Figure~\ref{fig:ethanol_msd_comparison}). We validated our analysis using a 1
-  ns simulation of a box of tip3p water molecules. As expected, since the
-  particles exhibit Brownian motion, the time-averaged and ensemble-averaged MSDs
-  agree with each within error (Figure~\ref{fig:water_box_msd_comparison}).
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -compare -nboot 2000 -a z
-% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
-  \includegraphics[width=\textwidth]{ethanol_msd_comparison.pdf}
-  \caption{}\label{fig:ethanol_msd_comparison}
-  \end{subfigure} 
-  \begin{subfigure}{0.45\textwidth}
-% Generated with msd.py -t traj_nojump.xtc -g npt.gro -r SOL -compare --fracshow 0.4 -nboot 2000 -a z
-% in directory: /home/bcoscia/Documents/Gromacs/Transport/Solvent/solvent_boxes/pure_water
-  \includegraphics[width=\textwidth]{water_box_msd_comparison.pdf}
-  \caption{}\label{fig:water_box_msd_comparison}
-  \end{subfigure} 
-  \caption{(a) The time-averaged and the ensemble-averaged MSDs for ethanol in
-	  an H\textsubscript{II} nanopore are not in agreement, implying non-ergodicity.
-	  (b) A box of tip3p water molecules is expected to be ergodic and it is shown to
-	  be true here because both MSDs are in agreement. }\label{fig:msd_comparison}
-  \end{figure}
-
-  \subsection*{Autocorrelation of steps}
-
-% From Sokolov paper: "Assigning different waiting times τ i to each step, and assuming that the
-% steps are uncorrelated as in a regular RW, gives rise to the CTRW model" -- I
-% might need to check autocorrelation of steps lengths when a hop occurs rather
-% than every time step. Not sure if there is enough data for that, but could check 
-% a particularly hoppy trajectory after longer simulation.
-
-  Based on the previous two sections, our model can likey be studied as a CTRW. 
-  However, it is still possible that our CTRW model might also be convoluted with
-  an FBM or a RWF process. In a pure CTRW, the steps are uncorrelated. 
-  Both FBM and RWF exhibit anti-correlated steps.
-
-  The steps in our system are not correlated. We showed this by calculating the
-  autocorrelation function (ACF) of the step lengths in the $z$-direction. The
-  ACF of a representative trajectory is shown in Figure~\ref{fig:eth_autocorrelation}.
-
-  \begin{figure}[!htb]
-  \centering
-% Generated with brownian_test.py -t PR_nojump.xtc -g PR.gro -r ETH (and appropriate uncommenting -- need to rework that script)
-% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
-  \includegraphics[width=0.8\textwidth]{eth_autocorrelation.pdf}
-  \caption{The autocorrelation function (right) of a representative ethanol
-	   center of mass $z$-coordinate trajectory (left) almost immediately decays to zero,
-	   indicating a complete loss of memory of it's previous position. Noise increases
-	   at large time lags due to decreased sampling.}\label{fig:eth_autocorrelation}
-  \end{figure}
+% BJC: the arguments in the following section aren't as strong as I want them to be. 
+% And not necessary for this paper.
+%
+%  \section{Choosing a transport model}\label{section:transport_model_selection}
+%
+%  We used the toolbox created by Meroz and Sokolov in order to justify our
+%  choice of transport model.\cite{meroz_toolbox_2015} The solutes in our systems
+%  exhibit anomalous transport properties characteristic of a Continuous Time
+%  Random Walk (CTRW). 
+%
+%  \subsection*{Mean Squared Displacement}
+%
+%  The general form of a mean squared displacement (MSD) curve is:
+%  \begin{equation}
+%	\langle x^2(t) \rangle \sim t ^ \alpha
+%	\label{eqn:msd}
+%  \end{equation}
+%  For brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq
+%  1$, the particle of interest exhibits anomalous diffusion. Values of $\alpha$
+%  greater than 1 give rise to superdiffusion, while values of $\alpha$ less than
+%  1 give rise to subdiffusion.
+%
+%  We can calculate the ensemble-averaged MSD curve by averaging the MSDs of
+%  each particle trajectory, where each MSD is calculated using:
+%  \begin{equation}
+%	\delta^2(t) = \| \mathbf{r}(t) - \mathbf{r}(0) \|^2
+%	\label{eqn:ensemble_msd}
+%  \end{equation}
+%  where $\|\cdot\|$ represents the Euclidean norm. 
+%
+%  The mean squared displacement of solutes in our model is a non-linear
+%  function of time, with $\alpha < 1$ which is indicative of anomalous
+%  subdiffusion. Figure \ref{fig:msd_power_law}a plots the ensemble-averaged MSD
+%  curve for 24 ethanol molecules diffusing in a 10 wt\% water H\textsubscript{II}
+%  LLC membrane system. We fit a power law of the form $Ae^{\alpha}$ to the MSD
+%  curve. We performed 2000 bootstrap trials by randomly sampling 24 MSD curves
+%  with replacement from the 24 total ethanol MSD curves. The bootstrapped average
+%  value of $\alpha$ is 0.75 for this system. 
+% 
+%  \begin{figure}[!htb]
+%  \centering
+%% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -ensemble -power_law -a z -nboot 2000
+%% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
+%  \includegraphics[width=0.8\linewidth]{msd_power_law.pdf}
+%  \caption{(a) We fit a curve with the form of Equation~\ref{eqn:msd} to the
+%	  ensemble-averaged MSD curve. (b) The average value of $\alpha$, obtained using
+%	  fits to MSDs calculated from bootstrapped ensembles, is less than 1 suggesting
+%	  that ethanol molecules in our model exhibit subdiffusive
+%	  behavior.}\label{fig:msd_power_law}
+%  \end{figure}
+%
+%  \subsection*{Ergodicity}
+%
+%  The ergodicity of a system can help us narrow down the possible anomalous
+%  diffusion mechanisms. In an ergodic system, the time-averaged behavior of an
+%  observable should yield the same result as the ensemble average of the same
+%  observable. Examples of anomalous diffusion processes that are ergodic include
+%  random walks on fractals (RWF) and fractional brownian motion (FBM).
+%  Non-ergodic systems generally give rise to CTRWs with the possibility of
+%  combination with a RWF and/or FBM.\cite{meroz_toolbox_2015} 
+%
+%  We tested the ergodicity of our system by comparing the ensemble-averaged
+%  and time-averaged MSD curves. We calculated the MSD of each ethanol trajectory
+%  using Equation~\ref{eqn:ensemble_msd} and a time-averaged algorithm: 
+%  \begin{equation}
+%	\delta^2(t) = \dfrac{1}{N-t} \sum_{i=0}^{N-t-1} \| \mathbf{r}(i + t) - \mathbf{r}(i) \|^2
+%  \end{equation}
+%  where N is the total number of simulation frames, and t represents the length
+%  of subinterval or number of frames per subinterval. We averaged the MSD curves
+%  from each trajectory in order to create final MSD plots.
+%
+%  The ethanol molecules exhibit non-ergodic behavior because their
+%  time-averaged and ensemble-averaged MSDs do not agree with each other
+%  (Figure~\ref{fig:ethanol_msd_comparison}). We validated our analysis using a 1
+%  ns simulation of a box of tip3p water molecules. As expected, since the
+%  particles exhibit Brownian motion, the time-averaged and ensemble-averaged MSDs
+%  agree with each within error (Figure~\ref{fig:water_box_msd_comparison}).
+%
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -compare -nboot 2000 -a z
+%% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
+%  \includegraphics[width=\textwidth]{ethanol_msd_comparison.pdf}
+%  \caption{}\label{fig:ethanol_msd_comparison}
+%  \end{subfigure} 
+%  \begin{subfigure}{0.45\textwidth}
+%% Generated with msd.py -t traj_nojump.xtc -g npt.gro -r SOL -compare --fracshow 0.4 -nboot 2000 -a z
+%% in directory: /home/bcoscia/Documents/Gromacs/Transport/Solvent/solvent_boxes/pure_water
+%  \includegraphics[width=\textwidth]{water_box_msd_comparison.pdf}
+%  \caption{}\label{fig:water_box_msd_comparison}
+%  \end{subfigure} 
+%  \caption{(a) The time-averaged and the ensemble-averaged MSDs for ethanol in
+%	  an H\textsubscript{II} nanopore are not in agreement, implying non-ergodicity.
+%	  (b) A box of tip3p water molecules is expected to be ergodic and it is shown to
+%	  be true here because both MSDs are in agreement. }\label{fig:msd_comparison}
+%  \end{figure}
+%
+%  \subsection*{Autocorrelation of steps}
+%
+%% From Sokolov paper: "Assigning different waiting times τ i to each step, and assuming that the
+%% steps are uncorrelated as in a regular RW, gives rise to the CTRW model" -- I
+%% might need to check autocorrelation of steps lengths when a hop occurs rather
+%% than every time step. Not sure if there is enough data for that, but could check 
+%% a particularly hoppy trajectory after longer simulation.
+%
+%
+%  Based on the previous two sections, our model can likey be studied as a CTRW. 
+%  However, it is still possible that our CTRW model might also be convoluted with
+%  an FBM or a RWF process. In a pure CTRW, the steps are uncorrelated. 
+%  Both FBM and RWF exhibit anti-correlated steps. 
+%
+%  The steps in our system are not correlated. We showed this by calculating the
+%  autocorrelation function (ACF) of the step lengths in the $z$-direction. The
+%  ACF of a representative trajectory is shown in Figure~\ref{fig:eth_autocorrelation}.  
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%% Generated with brownian_test.py -t PR_nojump.xtc -g PR.gro -r ETH (and appropriate uncommenting -- need to rework that script)
+%% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
+%  \includegraphics[width=0.8\textwidth]{eth_autocorrelation.pdf}
+%  \caption{The autocorrelation function (right) of a representative ethanol
+%	   center of mass $z$-coordinate trajectory (left) almost immediately decays to zero,
+%	   indicating a complete loss of memory of it's previous position. Noise increases
+%	   at large time lags due to decreased sampling.}\label{fig:eth_autocorrelation}
+%  \end{figure}
 

### 2019-03-15 Ben_Manuscripts/transport/Outline.tex
added comments to outline.
Updates

@@
 \usepackage{float}
+\usepackage{xr}
+
+\externaldocument[S-]{Supporting_Information}
 
@@
 	compounds.
+  \end{itemize}
+
+  %BJC1: copied from discussion. Need to work this in the right place
+  \begin{itemize}  
+  	\item Membranes, including that studied here, are often characterized 
+  	with size-exclusion experiments which emphasizes selectivity based on the ability
+  	to enter a given pore. 
+  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
+  	becomes of secondary importance since the primary purpose of these membranes is to 
+  	separate molecules whose sizes are on the same order as water.
+  	\item In order to handle complex waste streams with molecules of similar size,
+  	it is important to take advantage of material properties other than pore size. 
   \end{itemize}
@@
 
-  	\item Can we describe the transport mechanisms using pre-existing 
-  	mathematical models. \label{question:math}
-
-  	A mathematical model may provide additional insight into the transport
-  	mechanisms and, in future work, can help relate performance on the 
-  	timescales studied with MD to macroscopic timescales. We will use
-  	qualitative and semi-quantitative arguments in order to choose a 
-  	governing model.
+%  	\item Can we describe the transport mechanisms using pre-existing 
+%  	mathematical models. \label{question:math}
+%  	
+%  	A mathematical model may provide additional insight into the transport
+%  	mechanisms and, in future work, can help relate performance on the 
+%  	timescales studied with MD to macroscopic timescales. We will use
+%  	qualitative and semi-quantitative arguments in order to choose a 
+%  	governing model.
 
@@
 
-  Python scripts used to set up systems and conduct post-simulation trajectory analysis are
-  available online at \texttt{https://github.com/bencoscia/llcsim}.
-
-  \noindent We ran all molecular dynamics simulations and energy minimizations using 
-  GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-
-  \subsection*{System Setup}
+  Python scripts used to set up systems and conduct post-simulation trajectory 
+  analysis are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
+  The appropriate script to use for each of the following calculations is summarized
+  in Table~\ref{S-table:python_scripts} of the SI.
+
+  \noindent We ran all molecular dynamics simulations and energy minimizations 
+  using GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
+
+  \subsection*{System Setup}\label{method:system_setup}
 
@@
   \begin{itemize}
-	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
+	\item There is a 2:1 ratio of water in the pores versus in the tails for the 10 wt \% system.
 	\item The amount of water present in the tails may or may not be experimentally consistent
@@
 	will give issues with measurements and calculations.
-	\item See supporting info for water equilibration simulation data.
+	\item See section~\ref{S-section:water_content_equil} of the SI for further details on 
+	water equilibration in this system.
 	\item We iteratively adjusted the pore radius in our systems until the right amount of water
@@
 
-  \noindent We added 6 solute molecules to each pore of the equilibrated cross-linked
-  configuration.
+  \noindent To study a given solute, we added 6 solute molecules to each pore of the
+  equilibrated cross-linked configuration.
   \begin{itemize}
@@
 
-  \subsection*{Solute Parameterization}
+  \subsection*{Solute Parameterization}\label{method:parameterization}
 
@@
 	motion respectively.
+    % MRS1: time vs. ensemble MSD better in follow-up paper.
 	\item In practice, $\alpha$ corresponds to the growth of the \textit{ensemble}
@@
 
+  \subsection*{Molecular Size Determination}\label{method:molecular_size}
+
+  In order to determine an effective radius for each solute, we measured the 
+  maximum pairwise distance between atoms of each solute over the course of
+  a 2.5 ns simulation of solutes dissolved in a cubic box of water.
+  \begin{itemize}
+    \item Each box consisted of about 2100 water molecules and 6 solutes.
+    \item Although there exist more involved methods for determining the 
+    hydrodynamic radius~\cite{schultz_determination_1961}, we chose to use
+    a simpler and more intuitive metric since we are only interested in
+    observing trends in the solute mean squared displacement as a function
+    of solute size. 
+  \end{itemize}
+
   \subsection*{Dwell and Hop Length Distributions}\label{method:hops_and_dwells}
+
+  %MRS1: we probably only want enough do identify mechanism not to fit anything.  Think about minimum needed for physical understanding.
+  %BJC1: right, the following is the bear minimum if we want to mention dwell time and hop lengths at all. Otherwise this can be omitted.
 
@@
 
-  \subsection*{Radial Density Functions}
+  \subsection*{Radial Density Functions}\label{method:rdfs}
+  % BJC1: Should it be Radial Distribution Functions?
 
@@
 	small degree of tortuosity which disrupts the RDF calcuation 
-	\item We obtain the best RDF by constructing splines that run through the
-	pore centers.
+    % MRS1: can you report numerically the tortuosity?
+	\item We tried to mitigate the effects of tortuosity by calculating the RDF
+	with respect to splines that run through the pore centers.
 	\item We construct the splines by dividing the membrane into 10 slices
@@
 
-  \subsection*{Identification of Hydrogen Bonds}
-
+  \subsection*{Identification of Hydrogen Bonds}\label{method:hbonds}
+
+  %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
+  %we are not picking and choosing results (either consciously or unconsciously) 
   Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
@@
     package which allows us to directly check the validity of identified hydrogen bonds.
+    \item We tested the sensitivity of our conclusions to this definition in 
+    the Supporting Information.
     %BJC: might need to update this if something better exists for nitrogen 
@@
 
-  \subsection*{Coordination number}
-
-  We quantified the coordination of solutes with surrounding molecules.
-  \begin{itemize}
-  	\item For each frame, we counted the identities and number of
-  	coordinated molecules to a given solute based on a distance cut-off. 
+  \subsection*{Coordination number}\label{method:coordination}
+
+  We quantified the coordination of solute constituent atoms with sodium ions.
+  \begin{itemize}
+  	\item For each frame, we counted the number of coordinated molecules to a
+  	given solute atom based on a distance cut-off. 
+  	\item Using four different methods, Rowley and Roux observed peaks in the
+  	radial distribution function for sodium coordinated with water at an O-Na
+  	distance of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. 
+  	\item We used 2.5 \AA~as the distance cutoff.
   	\item We found that this approach is more useful than calculating the
@@
 
-  Using four different methods, Rowley and Roux observed peaks in the radial
-  distribution function for sodium coordinated with water at an O-Na distance 
-  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA~as
-  the distance cutoff.  % BJC: this might be too strict. I've seen literature where they define 3.2 angstroms as the cutoff
+  Using our procedure we found that sodium ions in a solution of tip3p water
+  coordinate with an average of 3.4 water molecules.
+  \begin{itemize}
+    \item We created a 4 x 4 x 4 nm cubic box of water with the GROMACS tool,
+    \texttt{gmx solvate}
+    \item We used \texttt{gmx genion} to replace water molecules with sodium
+    and chloride ions in order to create a 0.6 M NaCl solution.
+    \item We let the system simulate for 5 ns and reported the average
+    number of coordinated water molecules per frame after discarding the first ns of 
+    simulation. % need to actually do this
+    \item We found that the reported average value is not sensitive to NaCl
+    concentration (See Supporting Information)
+  \end{itemize}
 
@@
 
-  \subsection*{Structure and Transport of Membrane Constituents}\label{section:membrane_components}
-
-  %BJC: Probably do analysis on pure water system for this section.
+  \subsection*{Structure of Membrane Constituents}\label{section:membrane_components}
+
+  %BJC: Do analysis on pure water system for this section.
 
@@
   \end{subfigure}
+  %MRS1: explicitly state the normalization used for the RDF.
+  %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
   \caption{The radial densities of various monomer components paint a picture of the
@@
   \end{figure}
+
+  \subsection*{Mechanisms Governing Small Solute Transport}\label{section:mechanism_overview}
+
+  We observed transport of sodium, water and 20 other small polar solutes inside the
+  membrane nanopores. 
+  \begin{itemize}
+  	\item First, we will comment on transport of the membrane constituents, water and sodium,
+  	in a system absent of any additional solutes.
+%    \item There are significantly more water molecules and sodium ions in the membrane
+%    than solutes.
+    \item Then we will present the general trends that we observe among the set of 
+    solutes studied.
+  \end{itemize}
+
+  \subsubsection*{Water and Sodium Ions}\label{section:transport_water_sodium}
 
@@
   \begin{itemize}
-    \item In bulk water, it is estimated that sodium coordinates with 5.6 - 5.8 water
-    molecules~\cite{rowley_solvation_2012}
     \item In our system, on average, each sodium ion is coordinated to about 1.7 
@@
     carboxylate group.~\cite{ma_drastically_2019}
+    %MRS1: are ``head group oxygen'' atoms the same as carboxylate? Not clear. 
     \item On average, sodium ions coordinate with 0.5 head group oxygen atoms in the
@@
   % BJC: I can probably just report the averages rather than plot this
+  %MRS1: yeah, this is not really worth a graphic.
   \begin{figure}[!htb]
@@
 
-  \subsection*{Mechanisms Governing Small Solute Transport}\label{section:mechanism_overview}
+  \subsubsection*{Transport of Small Polar Solutes}\label{section:general_transport_solutes}
 
@@
   	implies that solute MSD should be inversely related to solute size.  % citation
+        %MRS1: can you plot on the figure what the relatioship SHOULD look like?  It sort of looks linear-ish (especially 5).
   	\item This behavior is not entirely surprising but worth emphasizing. 
@@
   	solute and solvent are of comparable size.
+        %MRS1: these points below seem more like intro points.
+
   	\item Membranes, including that studied here, are often characterized 
@@
   \end{figure}  
-
+  %MRS1: Having so much data here grapically is nice.
+ought to think how else data can be displayed.
+Perhaps figures with the dwell times as well?
+Depends on if those are being shown.
+2D scatter plots with average partitioning distance of solute vs.
+MSD?
+We should keep brainstorming which will be most relevant.
   \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
@@
   \end{subfigure}
+  %MRS1: nice graph!
   \caption{All solutes show subdiffusive transport behavior inside the membrane's
@@
   hydrogen bond donor solutes and monomer carboxylate groups. 
+  %MRS1: is there a way we can deconvolute these two-three mechanisms?
   \begin{itemize}
@@
     are 5 times more water molecules in the system.
+    %MRS1: carboxylate also has net negative charge - not just higher negative partial charge,
+    %also no extra neutralizing positive partial charge nearby.
     \item The carboxylate oxygen atoms have a slightly higher partial negative
@@
     to a sodium ion which decreases their availability to solutes.
+    %MRS1: this should lead to reduced ability to solvate positive things, but shouldn't reduce H-boonding that much?
   \end{itemize}
@@
     \item There are many cases in which polar groups bind to sodium ions for at
+    %MRS1: a 'few times steps' seems irrelevant.   
     least a few time steps. 
@@
 
+  %MRS1: I think maybe we want to keep this minimal. 
   \noindent The hopping and trapping mechanism exhibited by all solutes is characteristic of
@@
   	oxygen atoms combined with their lower partial charges.
+        %MRS1: also carboxylate has larger net charge.
+        %MRS1: note the partial chage is a moel thing
   	\item Butanol shows the largest preference towards hydrogen bonds with carboxylate 
@@
   	\item When solutes are buried in the pore walls, their MSDs are shorter.
+        %MRS1: is there enough data to establish this? How will it be graphed?  
   \end{itemize}
@@
   \end{subfigure}
+  %MRS: label the black line (tails? heads?)
   \caption{(a) The MSD of the simple alcohols decrease as a function of the solute size, however
@@
   % BJC: this subfigure is probably best suited for the supporting information.
-  \begin{subfigure}{\textwidth}
-  \centering
-  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
-  \caption{}\label{fig:dwell_hop_PG_GCL}
-  \end{subfigure}
+%  \begin{subfigure}{\textwidth}
+%  \centering
+%  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
+%  \caption{}\label{fig:dwell_hop_PG_GCL}
+%  \end{subfigure}
   \caption{(a) Glycerol, tetrose and ribose are densest close to the pore center because

### 2019-03-15 Ben_Manuscripts/transport/Supporting_Information.tex
Updates

@@
 \usepackage{float}
+\usepackage{xr}
+
+\externaldocument[M-]{Outline}
 
@@
   interaction between solutes which gave us a sufficient number of independent 
-  trajectories to observe and analyze. There are a negligible number of occurences
+  trajectories to observe and analyze. There are a negligible number of occurrences
   % BJC: not sure what the appropriate cut-off should be
@@
   molcules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interation}
+  \end{figure}
+
+  \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensisitivity}
+
+  In Section~\ref{M-method:hbonds} of the main text, we established geometric criteria for the 
+  identification of hydrogen bond interactions. Namely, if the distance between the donor,
+  D, and acceptor, A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less
+  than 30\degree, then we consider the interaction to be a consequence of hydrogen bonding.
+
+  We tested the sensitivity of this criteria to ensure that our conclusions
+  were not a strong function of the chosen criteria. In Figure~\ref{fig:hbond_sensitivity} we
+  plotted the results of the same calculation performed to create Figure~\ref{M-fig:multi_hbonds}
+  of the main text. We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
+  angle cut-off between 25 and 35 \degree.
+
+  As the distance and angle cut-offs are increased, there is a slight increase in the total
+  number of hydrogen bonds, which is primarily manifested by an increased number of multiple-hydrogen-bond
+  interactions. Using our most lenient set of criteria (d = 4.0 \AA~and $\theta$ = 35 $\degree$), glycerol,
+  tetrose and ribose all show instances where they simultaneously hydrogen bond with 4 head group atoms.
+  In the strictest case (d = 3.0 \AA~and $\theta$ = 25 \degree), ribose is the only solute with a 
+  detected instance of a quadruple hydrogen bond.
+
+  We can draw the same conclusions from any of the plots in Figure~\ref{fig:hbond_sensitivity}. 
+  \begin{enumerate}
+    \item An increased number of hydroxyl groups results in an increased number of hydrogen bond
+    interactions.
+    \item The number of multiple-hydrogen-bond interactions increases.
+    \item On average, propylene glcyol participates in more hydrogen bond interactions than 
+    ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)
+  \end{enumerate}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[trim={0 0.5cm 0.5cm 0.5cm}, clip, width=0.5\textwidth]{hbond_sensitivity_legend.pdf}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{hbond_sensitivity.pdf}
+  \end{subfigure}
+  \caption{We tested the sensitivity of our hydrogen bond detection to the chosen 
+  geometric criteria for hydrogen bonding. We varied the distance cut-off between 3.0 and
+  4.0 \AA, and varied the angle cut-off between 25 and 35 \degree.}\label{fig:hbond_sensitivity}
   \end{figure}

### 2019-03-18 Ben_Manuscripts/transport/Outline.tex
Updates to outline + supporting

@@
 
-  \subsection*{Dwell and Hop Length Distributions}\label{method:hops_and_dwells}
-
-  %MRS1: we probably only want enough do identify mechanism not to fit anything.  Think about minimum needed for physical understanding.
-  %BJC1: right, the following is the bear minimum if we want to mention dwell time and hop lengths at all. Otherwise this can be omitted.
-
-  \noindent We measured the distribution of dwell times and hop lengths in order to test
-  the hypothesis that solutes follow a CTRW process.
-  \begin{itemize}
-	\item We used the \texttt{ruptures} python package in order to identify
-	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
-%	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
-%	function, cost function penalty	tolerance, number of dimensions used)
-	\item The corresponding hop lengths and dwell times between break points were 
-	used to construct empirical distributions.
+%  \subsection*{Dwell and Hop Length Distributions}\label{method:hops_and_dwells}
+%
+%  %MRS1: we probably only want enough do identify mechanism not to fit anything.  Think about minimum needed for physical understanding.
+%  %BJC1: right, the following is the bear minimum if we want to mention dwell time and hop lengths at all. Otherwise this can be omitted.
+%
+%  \noindent We measured the distribution of dwell times and hop lengths in order to test
+%  the hypothesis that solutes follow a CTRW process.
+%  \begin{itemize}
+%	\item We used the \texttt{ruptures} python package in order to identify
+%	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
+%%	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
+%%	function, cost function penalty	tolerance, number of dimensions used)
+%	\item The corresponding hop lengths and dwell times between break points were 
+%	used to construct empirical distributions.
+%  \end{itemize}
+
+  \subsection*{The Stokes-Einstein Relationship}\label{method:stokes}
+
+  The Stokes-Einstein relationship expresses the diffusion coefficient of 
+  a hard spherical particle as a function inversely related to its radius.
+  \begin{itemize}
+  	\item $D = \dfrac{k_bT}{6\pi\eta r}$ where $k_b$ and $T$ are Boltzmann
+  	constant and the system temperature respectively and $\eta$ is the 
+  	system's viscosity.
+  	\item For calculation relevant to this study, we assume that the viscosity
+  	is constant.
+  	\item Additionally, we will apply the relationship to solute MSDs which is
+  	valid because all trajectories are of the same length.
+  	\item It is well-known that the relationship breaks down when solute size becomes
+  	on the order of solvent size because the solute can no longer be treated
+  	as a non-interacting hard sphere. 
+  \end{itemize}
+
+  Gierer and Wirtz introduced a microfriction correction factor in order to 
+  address this issue. 
+  \begin{itemize}
+    \item They proposed that $D = \dfrac{k_bT}{6\pi\eta fr}$
+    %\item Where $f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}$
+    \item Where $f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}$
+    \item and $r_1$ and $r_2$ are the radii of the solute and solvent molecules
+    respectively.
   \end{itemize}
@@
 	\item Although the pores are often described as straight, they have a
-	small degree of tortuosity which disrupts the RDF calcuation 
+	small degree of tortuosity which disrupts the RDF calcuation.
     % MRS1: can you report numerically the tortuosity?
+    % BJC1: added at end of paragraph after introduction of splines since tortuosity calculation uses splines.
 	\item We tried to mitigate the effects of tortuosity by calculating the RDF
 	with respect to splines that run through the pore centers.
-	\item We construct the splines by dividing the membrane into 10 slices
-	in the $z$-direction. Within each slice, we calculate the location of 
-	the pore centers based on the average location of the aromatic rings
-	that make up the monomer head groups.
-	\item When calculating the RDF, the radial distance from the pore center
+%    \item We construct the splines by dividing the membrane into 10 slices
+%	in the $z$-direction. Within each slice, we calculate the location of 
+%	the pore centers based on the average location of the aromatic rings
+%	that make up the monomer head groups.
+	\item Each spline consists of 10 points, equally spaced in the $z$-direction, whose
+    ($x$, $y$) coordinates are defined based on the center of mass of all head
+    groups closest, in $z$, to the given point.
+	\item When calculating RDFs, the radial distance from the pore center
 	is based on the distance between the solute center-of-mass and the linearly
@@
 	on the spline.
+	\item Using the splines, we calculated the tortuosity of the 
+	pores by calculating the ratio $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is 
+    the length of the unit cell in the $z$-direction. 
+    \item The average tortuosity of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 
+    5 and 10 wt \% systems respectively. 
+%    \item Although the value of tortuosity is low, the author's experience suggests
+%    that a spline is still justified.	
   \end{itemize}
@@
     \item We tested the sensitivity of our conclusions to this definition in 
-    the Supporting Information.
+    Section~\ref{S-section:hbond_sensitivity} of the SI.
     %BJC: might need to update this if something better exists for nitrogen 
@@
     \item We found that the reported average value is not sensitive to NaCl
-    concentration (See Supporting Information)
+    concentration (See section~\ref{S-section:coord_number} of the SI)
   \end{itemize}
@@
   \subsection*{Structure of Membrane Constituents}\label{section:membrane_components}
+
+  Before beginning the analysis of transport behavior, it is important to elucidate
+  the topology of the membrane pores.
 
@@
 
-  %BJC: I'm not sure if would be better to normalize the densities so that the
-  % shape of the sodium density is more pronounced
+  % BJC1: Should I show a dry system?
   \begin{figure}[!htb]
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.415\textwidth}
   \includegraphics[width=\textwidth]{component_density_5wt.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.15\textwidth}
+  \vspace{-0.5cm}
+  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
+  \label{fig:monomer_color_coded}
+  \end{subfigure}
+  \begin{subfigure}{0.415\textwidth}
   \includegraphics[width=\textwidth]{component_density_10wt.pdf}
@@
   \end{subfigure}
-  %MRS1: explicitly state the normalization used for the RDF.
+
   %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
+  %BJC1: tried it out. Seems like a good addition.
   \caption{The radial densities of various monomer components paint a picture of the
   pore topology where the pore centers are primarily composed of water and sodium ions.
-  The 5 wt \% system (a) appears to be much more crowded by monomers than the 
-  10 wt \% system (b). Head groups in (a) are densest closer to the pore center than
-  in (b). A small amount of tail components find their way close to the pore center 
-  of the 5 wt \% system. }\label{fig:component_densities}
+  All RDFs represent the number of atoms located at a given distance from the pore center
+  normalized by the volume of the annular bin 
+  to which they belong. The 5 wt \% system (a) appears to be much more crowded by monomers
+  than the 10 wt \% system (b). Head groups in (a) are densest about 0.2 nm closer to the
+  pore center than in (b). A small amount of tail components find their way close to the 
+  pore center of the 5 wt \% system.
+  }\label{fig:component_densities}
   \end{figure}
@@
   \begin{itemize}
-    \item In our system, on average, each sodium ion is coordinated to about 1.7 
-    water molecules in the 10 wt \% system and 1.15 water molecules in the 5 wt\% 
-    system.
+    \item Compared to 3.4 coordinated water molecules in bulk solution (see 
+    section~\ref{method:coordination}), sodium ions in our system are, on average,
+    coordinated to about 1.7 water molecules in the 10 wt \% system and 1.2 water
+    molecules in the 5 wt\% system.
     \item The low levels of water coordination under confinement are likely driven
@@
     \item A dehydrated sodium ion is not shielded from the negatively charged 
-    carboxylate group.~\cite{ma_drastically_2019}
-    %MRS1: are ``head group oxygen'' atoms the same as carboxylate? Not clear. 
-    \item On average, sodium ions coordinate with 0.5 head group oxygen atoms in the
-    10 wt \% water system and 0.4 head group oxygen atoms in the 5 wt \% water system. 
+    carboxylate group.~\cite{ma_drastically_2019}. 
+    \item On average, sodium ions coordinate with 0.5 carboxylate group oxygen atoms in the
+    10 wt \% water system and 0.4 carboxylate oxygen atoms in the 5 wt \% water system. 
     % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
@@
   %MRS1: yeah, this is not really worth a graphic.
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
-  \caption{}\label{fig:na_water_coordination}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
-  \caption{}\label{fig:na_hg_coordination}  % No caption since this probably won't be a figure
-  \end{subfigure}
-  \end{figure}
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
+%  \caption{}\label{fig:na_water_coordination}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
+%  \caption{}\label{fig:na_hg_coordination}  % No caption since this probably won't be a figure
+%  \end{subfigure}
+%  \end{figure}
 
@@
   \begin{itemize}
-  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
-  	\item There are numerous examples of solutes in our study that do not 
-  	follow the behavior set forth by the Stokes-Einstein equation which 
-  	implies that solute MSD should be inversely related to solute size.  % citation
-        %MRS1: can you plot on the figure what the relatioship SHOULD look like?  It sort of looks linear-ish (especially 5).
-  	\item This behavior is not entirely surprising but worth emphasizing. 
-  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
-  	the solute radius is much larger than the solvent, should break down once
-  	solute and solvent are of comparable size.
-        %MRS1: these points below seem more like intro points.
-
-  	\item Membranes, including that studied here, are often characterized 
-  	with size-exclusion experiments which emphasizes selectivity based on the ability
-  	to enter a given pore. 
-  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
-  	becomes of secondary importance since the primary purpose of these membranes is to 
-  	separate molecules whose sizes are on the same order as water.
-  	\item In order to handle complex waste streams with molecules of similar size,
-  	it is important to take advantage of material properties other than pore size. 
+  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt}
+  	and~\ref{fig:msd_radius_10wt}.
+  	\item Based on the Stokes-Einstein relationship, it is expected that
+  	the solute MSDs should be inversely related to solute size.
+  	\item Once solute and solvent are of comparable size, the relationship breaks
+  	down and tends to underestimate the MSD. 
+  	\item Gierer and Wirtz introduced a microfriction factor as theoretical
+  	correction.
+%  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
+%  	the solute radius is much larger than the solvent, should break down once
+%  	solute and solvent are of comparable size.
+  	\item Assuming that the Stokes-Einstein relationship is no longer valid 
+  	for solutes with radius less than x nm, we fit the Stokes-Einstein relationship 
+  	with and without the correction factor making sure that the two curves intersected
+  	at x nm and that the corrected line passed through the highest MSD data point, methanol. %BJC1: need a justified value for x. Can also show its insensitivity to choice of intersection point.
+  	\item We believe methanol is subject to the least hindrance due to its 
+  	size 
+  	\item Although both curves are approximations, they illustrate that
+  	the majority of solutes in our study show lower than expected MSDs. 
+%  	\item There are numerous examples of solutes in our study that do not 
+%  	follow the behavior set forth by the Stokes-Einstein equation which 
+%  	implies that solute MSD should be inversely related to solute size.  % citation
+%    % MRS1: can you plot on the figure what the relatioship SHOULD look like?  It sort of looks linear-ish (especially 5).
+%  	\item This behavior is not entirely surprising but worth emphasizing. 
+	%BJC1: below moved to intro
+%  	\item Membranes, including that studied here, are often characterized 
+%  	with size-exclusion experiments which emphasizes selectivity based on the ability
+%  	to enter a given pore. 
+%  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
+%  	becomes of secondary importance since the primary purpose of these membranes is to 
+%  	separate molecules whose sizes are on the same order as water.
+%  	\item In order to handle complex waste streams with molecules of similar size,
+%  	it is important to take advantage of material properties other than pore size. 
 %  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
@@
   %BJC: missing a few since those simulations just got started
+  %BJC1: wondering if I should add some kind of confidence interval to the Stoke-Einstein plots. Based on the errorbars of methanol
+  %BJC1: should the points be labeled with residue names?
   \begin{subfigure}{0.45\textwidth}
@@
   smaller than those of the solutes in the 10 wt \% water system (b). The
-  MSDs are not a monotonic function of molecular size (c and d).}\label{fig:msds}
+  MSDs are not a monotonic function of molecular size (c and d). A significant
+  number of solute MSDs fall below the theoretical lines predicted by the 
+  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.}\label{fig:msds}
   \end{figure}  
@@
   \end{itemize}
+
+  % Stokes-Einstein underestimates diffusion coefficient for small molecules.
+  % r down, f down, D up
+  % Stokes-Einstein breaks down for particles less ___ nm in size
+  % Fit corrected line through methanol.
+  % Make stokes einstein intersect corrected line at breakdown radius
 

### 2019-03-18 Ben_Manuscripts/transport/Supporting_Information.tex
Updates to outline + supporting

@@
 
+  \subsection{Pore Splines}\label{section:splines}
+
+  We captured the apparent $z$-dependence of the pore center locations by
+  constructing splines running through each pore (See Figure~\ref{fig:spline}).
+  Each spline consists of 10 points, equally spaced in the $z$-direction, whose
+  ($x$, $y$) coordinates are defined based on the center of mass of all head
+  groups closest, in $z$, to the given point.
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=0.45\textwidth]{spline.pdf}
+  \caption{We traced the center of each pore as a function of $z$ using a spline (pink
+  line). We constructed the spline in each pore using 10 points (pink spheres) whose
+  positions we defined based on the center of mass of the head groups in closest proximity
+  to the spline point in the $z$-direction.}\label{fig:spline}
+  \end{figure}
+
+  We calculated the tortuosity, $\tau$, of the pores by calculating the 
+  ratio $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is 
+  the length of the unit cell in the $z$-direction.
+
   \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensisitivity}

### 2019-03-18 Ben_Manuscripts/transport/figures/msd_radius.py

@@ -7,7 +7,7 @@ import sqlite3 as sql
 path = "/home/bcoscia/PycharmProjects/LLC_Membranes/LLC_Membranes/analysis/"
 connection = sql.connect('%s/size.db' % path)
 crsr = connection.cursor()
-wt = 10 
+wt = 5 
 
 simple_alcohols = False 
 if simple_alcohols:
@@ -69,11 +69,40 @@ r_order = np.array([rnames.index(i) for i in names])
 
 #plt.scatter(msd, r[r_order])
 plt.errorbar(r[r_order], msd, yerr=(msd_lower, msd_upper), xerr=r_std[r_order], fmt='o', elinewidth=0.5, ecolor='black')
+
+# Theoretical Calcuations
+water_size = 0.151391485766 # from ACH cubic box. std: 0.000407801323403
+
+r_theoretical = np.linspace(0.25, 0.68, 100)
+#r_theoretical = np.linspace(min(r), 10, 1000)
+
+# Corrected version first
+alpha = water_size / r_theoretical # radius of solute (residue) to solvent (water) 
+f = ((3 * alpha / 2) + (1 / (1 + alpha)))**-1  # f as function of alpha
+alpha_max = water_size / r[r_order][np.argmax(msd)]  # alpha for solute with max msd
+fmax = ((3 * alpha_max / 2) + (1 / (1 + alpha_max)))**-1  # f for solute with max msd
+a = fmax * np.max(msd) * r[r_order][np.argmax(msd)]  # make the curve pass through the max msd point
+
+# Make Stokes-Einstein intersect with correction at r_intersect
+r_intersect = 5 # where we want stokes-einstein and corrected stoke-einstein to intersect
+
+alpha_intersect = water_size / r_intersect
+f_intersect = ((3 * alpha_intersect / 2) + (1 / (1 + alpha_intersect)))**-1
+y_intersect = a / (f_intersect * r_intersect)
+print(y_intersect)
+y_stokes = y_intersect * r_intersect / r_theoretical
+y_gierer_wirtz = a / (r_theoretical * f)
+
+plt.plot(r_theoretical, y_stokes, '--', color='black', label='Stokes-Einstein')
+plt.plot(r_theoretical, y_gierer_wirtz, '--', color='blue', label='Gierer and Wirtz correction')
+
+# Plot formatting
 plt.xlabel('Radius (nm)', fontsize=14)
[…]

### 2019-03-18 LLC_Membranes/llclib/physical.py

@@ -456,14 +456,14 @@ def trace_pores(pos, box, npoints, npores=4, progress=True, save=True, savename=
                     shift = transform.translate(pore[atom_indices, :], before, center[t, :])  # shift everything to towards the center
 
                     for i in range(shift.shape[0]):  # check if the points are within the bounds of the unitcell
-                        if not bounds[t].contains_point(shift[i, :2]):
+                        while not bounds[t].contains_point(shift[i, :2]):
                             shift[i, :] = put_in_box(shift[i, :], box[t, 0, 0], box[t, 1, 1], m[t], angle[t])  # if its not in the unitcell, shift it so it is
 
                     c = [np.mean(shift, axis=0)]
 
                     centers[t, p, l - 1, :] = transform.translate(c, center[t, :], before)  # move everything back to where it was
 
-                    if not bounds[t].contains_point(centers[t, p, l - 1, :]):  # make sure everything is in the box again
+                    while not bounds[t].contains_point(centers[t, p, l - 1, :]):  # make sure everything is in the box again
                         centers[t, p, l - 1, :] = put_in_box(centers[t, p, l - 1, :], box[t, 0, 0], box[t, 1, 1], m[t], angle[t])
 
         if single_frame:

### 2019-03-19 Ben_Manuscripts/transport/Outline.tex
Outline updates

@@
   The Stokes-Einstein relationship expresses the diffusion coefficient of 
-  a hard spherical particle as a function inversely related to its radius.
-  \begin{itemize}
-  	\item $D = \dfrac{k_bT}{6\pi\eta r}$ where $k_b$ and $T$ are Boltzmann
-  	constant and the system temperature respectively and $\eta$ is the 
-  	system's viscosity.
-  	\item For calculation relevant to this study, we assume that the viscosity
-  	is constant.
-  	\item Additionally, we will apply the relationship to solute MSDs which is
-  	valid because all trajectories are of the same length.
-  	\item It is well-known that the relationship breaks down when solute size becomes
+  a hard spherical particle as a function that is inversely related to the
+  particle's radius:
+  \begin{itemize}
+  	\item $D = \dfrac{k_bT}{6\pi\eta r}$
+  	\item where $k_b$ and $T$ are the Boltzmann	constant and the system 
+  	temperature respectively and $\eta$ is the system's viscosity.
+  	\item For the largely demonstrative calculations relevant to this study, 
+  	we assume that the system viscosity is constant since we only make minor
+  	changes to the membrane's composition and accurately assessing the viscosity
+  	in a complex and inhomogeneous system such as ours is a challenge by itself.
+  	\item Additionally, rather than calculate $D$, we will apply the relationship
+  	to analyze solute MSDs, which is valid because all trajectories are of the same
+  	length.
+  \end{itemize}
+
+  \noindent It is well-known that the relationship breaks down when solute size becomes
   on the order of solvent size because the solute can no longer be treated
-  	as a non-interacting hard sphere. 
-  \end{itemize}
-
-  Gierer and Wirtz introduced a microfriction correction factor in order to 
+  as a non-interacting hard sphere. % citation
+  \begin{itemize}
+    \item Gierer and Wirtz introduced a microfriction correction factor in order to 
     address this issue. 
-  \begin{itemize}
     \item They proposed that $D = \dfrac{k_bT}{6\pi\eta fr}$
@@
     package which allows us to directly check the validity of identified hydrogen bonds.
-    \item We tested the sensitivity of our conclusions to this definition in 
-    Section~\ref{S-section:hbond_sensitivity} of the SI.
+    \item In section~\ref{S-section:hbond_sensitivity} of the SI, we show that our 
+    conclusions are insensitive to this definition within a reasonable range.
     %BJC: might need to update this if something better exists for nitrogen 
@@
     \item Figure~\ref{fig:component_densities} plots the densities of each
-    membrane constituent.
+    membrane constituent in the 5 and 10 wt \% systems.
     \item Water is densest at the center of each pore. 
-    \item Sodium ions are densest between the pore center and the peak head group density.
+    \item Sodium ions are densest between the pore center and the peak head group density (black dashed line).
     \item The peak density of sodium ions is not at the pore center in either case
@@
     that occupy the pore center.
+    \item Based on these observations, we expect solute transport to be fastest 
+    in the 10 wt \% system.
   \end{itemize}
@@
   All RDFs represent the number of atoms located at a given distance from the pore center
-  normalized by the volume of the annular bin 
-  to which they belong. The 5 wt \% system (a) appears to be much more crowded by monomers
-  than the 10 wt \% system (b). Head groups in (a) are densest about 0.2 nm closer to the
-  pore center than in (b). A small amount of tail components find their way close to the 
-  pore center of the 5 wt \% system.
+  normalized by the volume of the annular bin to which they belong. The pores of the 5 
+  wt \% system (a) appears to be much more crowded by monomers than the 10 wt \% system (b).
+  Head groups in (a) are densest about 0.2 nm closer to the pore center than in (b). 
+  A small amount of tail components find their way close to the pore center of the 5 wt \% system.
   }\label{fig:component_densities}
@@
     in part by favorable interactions between sodium ions and carboxylate head groups.
-    \item A dehydrated sodium ion is not shielded from the negatively charged 
+    \item A dehydrated sodium ion is not well shielded from the negatively charged 
     carboxylate group.~\cite{ma_drastically_2019}. 
@@
 
-  \noindent The MSDs are not a monotonic function of solute size.
+  \noindent The MSDs depend on more than just solute size.
   \begin{itemize}
@@
   	and~\ref{fig:msd_radius_10wt}.
-  	\item Based on the Stokes-Einstein relationship, it is expected that
-  	the solute MSDs should be inversely related to solute size.
-  	\item Once solute and solvent are of comparable size, the relationship breaks
-  	down and tends to underestimate the MSD. 
-  	\item Gierer and Wirtz introduced a microfriction factor as theoretical
-  	correction.
+%  	\item Based on the Stokes-Einstein relationship, it is expected that
+%  	the solute MSDs should be inversely related to solute size.
+%  	\item Once solute and solvent are of comparable size, the relationship breaks
+%  	down and tends to underestimate the MSD. 
+%  	\item Gierer and Wirtz introduced a microfriction factor as theoretical
+%  	correction.
 %  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
@@
   	\item Assuming that the Stokes-Einstein relationship is no longer valid 
-  	for solutes with radius less than x nm, we fit the Stokes-Einstein relationship 
+  	for solutes with a radius less than x nm, we fit the Stokes-Einstein relationship 
   	with and without the correction factor making sure that the two curves intersected
   	at x nm and that the corrected line passed through the highest MSD data point, methanol. %BJC1: need a justified value for x. Can also show its insensitivity to choice of intersection point.
-  	\item We believe methanol is subject to the least hindrance due to its 
-  	size 
+  	\item We believe methanol is subject to the least hindrance due its small
+  	size and relatively fast motion.
   	\item Although both curves are approximations, they illustrate that
   	the majority of solutes in our study show lower than expected MSDs. 
+  	\item In most cases, the predicted MSDs even fall below the 
+  	conservative Stokes-Einstein estimate.
+  	\item It is clear that more complex mechanisms determine the MSDs of
+  	these solutes.
 %  	\item There are numerous examples of solutes in our study that do not 
@@
 
-  %BJC: need to check whether sodium ion association is exhibited by all solutes
   In addition to solute trapping in dense monomer regions, we observe a second
   trapping mechanism caused by preferential hydrogen bonding between 
-  hydrogen bond donor solutes and monomer carboxylate groups. 
+  hydrogen bond donor solutes and monomer head groups. 
   %MRS1: is there a way we can deconvolute these two-three mechanisms?
   \begin{itemize}
-    \item Of the time spent donating hydrogen atom(s), x \% of the hydrogen
-    bonds occur between solutes and carboxylate groups as opposed to solutes
-    with water. 
-    \item This shows a high preference for the carboxylate anions since there
-    are 5 times more water molecules in the system.
+    \item To continue with our ethanol example, we observe that the 24 ethanol 
+    molecules donate an average of 15.7 hydrogen bonds per frame and accept 
+    0.6 hydrogen bonds per frame.
+    % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and 
+    % ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
+    \item On average, 40 \% of hydrogen bonds donated by ethanol go to 
+    carboxylate head groups, 25 \% go to the ether linkages between the tails and
+    the head groups and the remaining 35 \% to water.
+%    \item This is significant because there are many more water molecules in
+%    the pores than there are carboxylate groups.  
+%    \item Of the time spent donating hydrogen atom(s), 53 \% of the hydrogen
+%    bonds occur between solutes and carboxylate groups as opposed to solutes
+%    with water. 
+%    \item This shows a high preference for the carboxylate anions since there
+%    are 5 times more water molecules in the system.  % BJC1: more like 3 times more water molecules because many are in the tails.
     %MRS1: carboxylate also has net negative charge - not just higher negative partial charge,
     %also no extra neutralizing positive partial charge nearby.
-    \item The carboxylate oxygen atoms have a slightly higher partial negative
-    charge than water molecules.
+    \item There are less carboxylate oxygen atoms in the pore than there are water
+    molecules yet more hydrogen bonds are donated to them.
+    \item The stability of hydrogen bonds with carboxylate oxygen atoms is likely
+    high since the oxygen atoms have a negative charge with no neutralizing positive
+    charges nearby.
     \item Additionally, on average, each sodium ion is coordinated to 1.7 water
-    molecules. Roughly all of the water in the pore region is usually coordinated
-    to a sodium ion which decreases their availability to solutes.
-    %MRS1: this should lead to reduced ability to solvate positive things, but shouldn't reduce H-boonding that much?
-  \end{itemize}
-
-  Finally, we see instances of solutes which become immobilized or slowed by 
+    molecules meaning an appreciable fraction of the water molecules occupying 
+    the pore region are usually coordinated to a sodium ion which decreases 
+    their availability to accept hydrogen bonds from solutes.
+    % MRS1: this should lead to reduced ability to solvate positive things, but 
+    % shouldn't reduce H-bonding that much?
+    % BJC1: I think that it takes away acceptor oxygen atoms since they are occupied
+    % by sodium. The hydrogen atoms of water could still hbond but I'm just talking
+    % about ethanol donating to water, for which opportunities should be suppressed.
+  \end{itemize}
+
+  Finally, we see instances of solutes that become immobilized or slowed by 
   association with sodium counterions. 
   \begin{itemize}
-    \item Much like water, the polarity of the solutes leaves partial negative
-    charges which are stabilized through electrostatic interactions with sodium ions.
+    \item Much like water, the polarity of the solutes creates regions of high
+    electron density, modeled using partial negative charges, which are stabilized
+    through electrostatic interactions with sodium ions.
     \item There are many cases in which polar groups bind to sodium ions for at
-    %MRS1: a 'few times steps' seems irrelevant.   
-    least a few time steps. 
+    least a short period of time. 
     \item There are some cases where solutes become immobilized for long periods
@@
     \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
-    within 2.5 \AA of a sodium ion for the entire length of a trapping occurence.
+    within 2.5 \AA~of a sodium ion for the entire length of a trapping occurence.
   \end{itemize}
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}
-  \caption{The oxygen atom of methanol stays bound to the same sodium ion for
+  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
+  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
   the majority of the trapping occurence between 400 and 600 ns. Regions
   highlighted red or blue indicate times when methanol's oxygen atom is within 
-  2.5 \AA~of a sodium ion. The color of the shaded regions is switched every time
+  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
   the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
@@
   %MRS1: I think maybe we want to keep this minimal. 
-  \noindent The hopping and trapping mechanism exhibited by all solutes is characteristic of
-  a continuous time random walk (CTRW) model.	
-  \begin{itemize}
-  	\item The length of entrapment follows a power law distribution 
-  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
-  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
-  	\item Power law distributed dwell times are responsible for the ageing phenomenon
-  	which causes the slope of the MSD curve to decrease with increasing measurement
-  	time because longer dwell times are sampled.  %BJC: might need to reword this a bit 
- 	\item Although these observed distributions strongly support a CTRW model, the time-averaged
- 	MSD of a pure CTRW should be linear which is not the case.~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
-  \end{itemize}
-
-%  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
-  \noindent Transport may be better described by a subordinated fractional brownian motion 
-  (sFBM) model.
-  \begin{itemize}
-  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
-  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Is there a better word?
-  	\item The negative autocovariance at low values of k indicates anti-correlation
-  	between hops. 
-  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
-  	decay to zero immediately.
-  	\item Although the autocovariance function is relatively noise, due to the somewhat small
-  	number of hops observed over the course of each solute trajectory, there is the least 
-  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
-  	all solutes molecules. % Can put error bars on points
-  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
-  	motion where the leading process is a CTRW with hops whose direction is dictated by the parent
-  	process, FBM.
-  	\item Future publications will focus on modeling the solute's transport characteristics
-  	with an sFBM model
-  	\item We will draw on these observations only in a qualitative sense for the remainder of this work.
-  \end{itemize}
-
-  %BJC: seems like the MSD becomes linear at long times. Perhaps due to loss of memory with time.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\linewidth]{example_powerlaw.pdf}
-  \caption{}\label{fig:example_powerlaw}
-  \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\linewidth]{example_hop_dist.pdf}
-  \caption{}\label{fig:example_hop_dist}
-  \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\linewidth]{example_autocovariance.pdf}
-  \caption{}\label{fig:example_autocovariance}
-  \end{subfigure}
-  \caption{(a) The distribution of dwell times resembles a power law distribution. 
-  (b) The distribution of hop lengths appears Gaussian. (c) Hops are anti-correlated
-  to their previous hop as indicated by the negative value of the autocovariance 
-  function at $k$ = 1.}\label{fig:examples}
-  \end{figure}
+  %BJC1: Leaving out for now
+%  \noindent The hopping and trapping mechanism exhibited by all solutes is characteristic of
+%  a continuous time random walk (CTRW) model.	
+%  \begin{itemize}
+%  	\item The length of entrapment follows a power law distribution 
+%  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
+%  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
+%  	\item Power law distributed dwell times are responsible for the ageing phenomenon
+%  	which causes the slope of the MSD curve to decrease with increasing measurement
+%  	time because longer dwell times are sampled.  %BJC: might need to reword this a bit 
+% 	\item Although these observed distributions strongly support a CTRW model, the time-averaged
+% 	MSD of a pure CTRW should be linear which is not the case.~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
+%  \end{itemize}
+%  
+%%  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
+%  \noindent Transport may be better described by a subordinated fractional brownian motion 
+%  (sFBM) model.
+%  \begin{itemize}
+%  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
+%  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Is there a better word?
+%  	\item The negative autocovariance at low values of k indicates anti-correlation
+%  	between hops. 
+%  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
+%  	decay to zero immediately.
+%  	\item Although the autocovariance function is relatively noise, due to the somewhat small
+%  	number of hops observed over the course of each solute trajectory, there is the least 
+%  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
+%  	all solutes molecules. % Can put error bars on points
+%  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
+%  	motion where the leading process is a CTRW with hops whose direction is dictated by the parent
+%  	process, FBM.
+%  	\item Future publications will focus on modeling the solute's transport characteristics
+%  	with an sFBM model
+%  	\item We will draw on these observations only in a qualitative sense for the remainder of this work.
+%  \end{itemize}
+%  
+%  %BJC: seems like the MSD becomes linear at long times. Perhaps due to loss of memory with time.
+%
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\linewidth]{example_powerlaw.pdf}
+%  \caption{}\label{fig:example_powerlaw}
+%  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\linewidth]{example_hop_dist.pdf}
+%  \caption{}\label{fig:example_hop_dist}
+%  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\linewidth]{example_autocovariance.pdf}
+%  \caption{}\label{fig:example_autocovariance}
+%  \end{subfigure}
+%  \caption{(a) The distribution of dwell times resembles a power law distribution. 
+%  (b) The distribution of hop lengths appears Gaussian. (c) Hops are anti-correlated
+%  to their previous hop as indicated by the negative value of the autocovariance 
+%  function at $k$ = 1.}\label{fig:examples}
+%  \end{figure}
 
   \noindent The transport behavior exhibited by solutes in the 5 wt \% water systems
-  is similar to those shown by those in the 10 wt \% system however the timescales are
+  is similar to that shown by those in the 10 wt \% system however the timescales are
   much longer.
@@
 
-  The MSD of methanol, ethanol, propanol and butanol descends in order of 
-  their molecular weight, however, methanol travels faster than expected.  %BJC: find approximate relationship between MW and mobility
-  \begin{itemize}
-    \item The MSD of ethanol, propanol and butanol descend approximately
-    linearly as expected from the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
-    \item However, methanol travels considerably faster than suggested by the
-    relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
+%  The MSD of methanol, ethanol, propanol and butanol descends in order of 
+%  their size, however, the.
+%  \begin{itemize}
+%    \item The MSD of ethanol, propanol and butanol descend approximately
+%    linearly as expected from the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
+%    \item However, methanol travels considerably faster than suggested by the
+%    relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
+%  \end{itemize}
+
+  The MSDs of methanol, ethanol, propanol and butanol descend in order of 
+  their size.
+  \begin{itemize}
+    \item Using methanol as a reference, the other alcohols move slower than
+    expected according to both the pure Stokes-Einstein relationship and the
+    corrected relationship (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}).
   \end{itemize}
@@
   with the monomer head groups, but with varying preference towards hydrogen bonds with
-  the monomer carboxylate oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds}) caused
-  by increasing hydrophobic character.
+  the monomer carboxylate oxygen atoms over the ether oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds})
+  % caused by increasing hydrophobic character.
   \begin{itemize}
@@
   	oxygen atoms for all simple alcohols.
-  	\item This is largely due to the more highly crowded environment surrounding the ether
-  	oxygen atoms combined with their lower partial charges.
-        %MRS1: also carboxylate has larger net charge.
-        %MRS1: note the partial chage is a moel thing
+  	\item This is largely due to the large net charge of the carboxylate groups as well
+  	as the more highly crowded environment surrounding the ether oxygen atoms. % combined with their lower electron density. % partial charges.
   	\item Butanol shows the largest preference towards hydrogen bonds with carboxylate 
@@
   	monomers, with hydrophilic components point towards the pore centers.
-  	\item When solutes are buried in the pore walls, their MSDs are shorter.
-        %MRS1: is there enough data to establish this? How will it be graphed?  
+  	%\item When solutes are buried in the pore walls, their MSDs are shorter.
   \end{itemize}
@@
   \centering
+  %BJC1: I'm not sure of figure (a) is necessary
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols.pdf}
+  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols_10wt.pdf}
   \caption{}\label{fig:msd_radius_simple_alcohol_rdf}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing butanol with highlighted O and C
+  \includegraphics[width=\linewidth]{butanol_CO.pdf}\lapbox[\width]{-2.85cm}{\raisebox{3cm}{\includegraphics[height=1.4cm]{butanol_labeled.pdf}}}
   \caption{}\label{fig:butanol_CO}

### 2019-03-19 LLC_Membranes/llclib/stats.py

@@ -5,7 +5,11 @@ from scipy import stats
 
 
 def confidence_interval(data, confidence):
-    """ Calculate confidence interval of data
+    """ Calculate confidence interval of data.
+
+    Plot these errorbars with plt.fill_between() as follows:
+    plt.fill_between(x, mean + error[1, :], mean - error[0, :])
+
 
     :param data: array of data trajectories [n_trajectories, n_data_points]
     :param confidence: percent confidence

### 2019-03-20 Ben_Manuscripts/transport/Outline.tex
Figure improvements + outline additions

@@
 
-  We need highly selective membranes in order to perform efficient separations.
+  We need highly selective and permeable membranes in order to perform efficient 
+  separations.
+  \begin{itemize}
+    \item Cleanup of fracking water
+    \item Removal of organic micropollutants, such as pesticides, pharmaceuticals,
+    and personal care products, from the drinking water supply.
+    \item Desalination
+    \item All of these separations are possible with current commercial membrane
+    separation techniques but they are too energy intensive to be worth the 
+    capital investment needed to start the processes.
+  \end{itemize}
+
+  Nanostructured membranes offer the potential for molecular-level design which
+  could overcome the limitations faced by conventional membrane technologies.
+  \begin{itemize}
+    \item Mitigation of stochastic aspects of membrane synthesis
+    \item Well-defined and uniform pores increase selectivity
+    \item Solute-specific separations.
+  \end{itemize}
 
@@
   sized pores and have the potential to disrupt conventional membrane separation
-  techniques by being selective based not only on size and charge, but on chemical
-  functionality as well.
-
-  We can only learn so much from experiment. MD can give us mechanistic insights with
-  atomistic resolution so that we can intelligently design new membranes for 
-  solute-specific separations.
-
-  In previous work, we determined the most likely structure of the hexagonal phase 
+  techniques by being selective based not only on solute size and charge, but on 
+  chemical functionality as well.
+  \begin{itemize}
+    \item Uniform pores lead to high selectivity
+    \item The hexagonal geometry is ideal for high permeability
+  \end{itemize}
+
+  While H\textsubscript{II} membranes have been synthesized and characterized
+  in a lab setting, there is a limit to the level of detail that can be obtained 
+  from experiment. 
+  \begin{itemize}
+  	\item The separation performance of these membranes has been primarily 
+  	characterized with size-exclusion experiments which emphasizes selectivity
+  	based on the ability to enter a given pore. 
+  	\item While size-exclusion is a useful separation, it cannot 
+  	reliably purify a solution where the solute size is on the same order as water.
+%  	\item Once on the nm to sub-nm pore size regime, size-exclusion 
+%  	becomes of secondary importance since the primary purpose of these membranes is to 
+%  	separate molecules whose sizes are on the same order as water.
+%  	\item In order to handle complex waste streams with molecules of similar size,
+  	\item Therefore, it is important to take advantage of material properties other
+  	than pore size.
+  	\item Unfortunately, the complexity of LLC Membranes has obscured the interpretation 
+  	of experimental transport studies.
+  \end{itemize}
+
+  Molecular dyanmics (MD) simulation can give us mechanistic insights with atomistic
+  resolution so that we can directly observe small solute transport within LLC membrane
+  nanopores and intelligently design new membranes for solute-specific separations.
+
+  In our previous work, we determined the most likely structure of the hexagonal phase 
   formed by the monomer Na-GA3C11.
@@
 	compounds.
-  \end{itemize}
-
-  %BJC1: copied from discussion. Need to work this in the right place
-  \begin{itemize}  
-  	\item Membranes, including that studied here, are often characterized 
-  	with size-exclusion experiments which emphasizes selectivity based on the ability
-  	to enter a given pore. 
-  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
-  	becomes of secondary importance since the primary purpose of these membranes is to 
-  	separate molecules whose sizes are on the same order as water.
-  	\item In order to handle complex waste streams with molecules of similar size,
-  	it is important to take advantage of material properties other than pore size. 
   \end{itemize}
@@
 
+  In all RDF plots, we include the average RDF of the head groups as a reference.
+  \begin{itemize}
+    \item The head group RDF shown is the average of the head group RDFs for each
+    solute system in the plot.
+    \item We generated 95 \% confidence intervals by bootstrapping the frame-by-frame
+    RDFs obtained from both systems.
+  \end{itemize}
+
   \subsection*{Identification of Hydrogen Bonds}\label{method:hbonds}
@@
   Using our procedure we found that sodium ions in a solution of tip3p water
-  coordinate with an average of 3.4 water molecules.
+  coordinate with an average of 3.6 water molecules.
   \begin{itemize}
@@
     \item We used \texttt{gmx genion} to replace water molecules with sodium
-    and chloride ions in order to create a 0.6 M NaCl solution.
+    and chloride ions in order to create a 0.1 M NaCl solution.
     \item We let the system simulate for 5 ns and reported the average
@@
     simulation. % need to actually do this
-    \item We found that the reported average value is not sensitive to NaCl
-    concentration (See section~\ref{S-section:coord_number} of the SI)
+    % BJC1: NaCl starts to crystallize for higher concentrations leading to lower coordination numbers
+%    \item We found that the reported average value is not sensitive to NaCl
+%    concentration (See section~\ref{S-section:coord_number} of the SI)
   \end{itemize}
@@
 
-  \subsection*{Transport of Diols, Triols and Sugars}  % polyols instead of sugars?
+  \subsection*{Transport of Diols, Triols and Sugars}\label{section:polyols}
 
@@
     \item Tetrose, ribose and glycerol are densest close to the pore center. This is 
-    likely a result of their hydrophilicity and large size which prevents them from
-    partitioning into the head group region.
+    likely a consequence of both their hydrophilicity and large size which prevents
+    them from partitioning into the head group region.
     \item However, these extra hydroxyl groups facilitate a larger number of 
@@
     bonds with different hydrogen bond acceptors at the same time.
-    \item In some cases, all 4 hydroxyl groups of ribose are hydrogen bonded to monomer
+    \item In some cases, all 4 hydroxyl groups of ribose hydrogen bonded to monomer
     head groups simultaneously.
@@
     especially when there are many, however proximity to the pore center partially 
-    compensates for this effect in the cases of glycerol and tetrose.
+    compensates for this effect in the cases of glycerol and tetrose, causing them to
+    have relatively high MSDs for their size.
   \end{itemize}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.50\textwidth}
+  \vspace{-0.275cm}
   \includegraphics[width=\linewidth]{multi_hbonds.pdf}
@@
   they have a high number of hydrophilic groups and are relatively large. Ethylene glycol
-  and propylene glycol are densest close to the head group region. (b)The number of 
+  and propylene glycol are densest close to the head group region. (b) The number of 
   hydrogen bond interactions between solutes and monomers increases as solutes gain additional
-  hydroxyl groups. Often, multiple hydroxyl groups within a solute often hydrogen bond in
-  different locations simultaneously. Occasionally, all four hydroxyl groups
-  of Ribose (n = 4) are involved in a hydrogen bond interaction at the same time.}\label{fig:multi_hbonds}
+  hydroxyl groups. The number of hydrogen bonds made by a single solute in different locations
+  simultaneously, n, also increases with the number of hydroxyl groups. In the most extreme case,
+  all four hydroxyl groups of Ribose (n = 4) are involved in a hydrogen bond interaction at
+  the same time.}\label{fig:multi_hbonds}
   \end{figure}
@@
     density has a large peak near the monomer head groups relative to ethylene glycol.
-    \item Propylene glycol can form more highly stablized hydrogen bonds with carboxylate groups,
+    \item Propylene glycol can form more highly stabilized hydrogen bonds with carboxylate groups,
     explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
-    \item These observations are further reflected in its dwell and hop length distributions
-    (See Figure~\ref{fig:dwell_hop_PG_GCL}).
-    \item Propylene glycol exhibits longer dwell times and a narrower distribution of 
-    hop lengths than ethylene glycol. 
+%    \item These observations are further reflected in its dwell and hop length distributions
+%    (See Figure~\ref{fig:dwell_hop_PG_GCL}).
+%    \item Propylene glycol exhibits longer dwell times and a narrower distribution of 
+%    hop lengths than ethylene glycol. 
     \item Somewhat counterintuitively, there is a relatively high density of ethylene
@@
     their carbonyl group.
-    \item The fastest solute of this grouping, acetic acid (comparable to urea), is about
-    3 times faster than the slowest, acetone, but only about 10 \% smaller.
+    \item The fastest solutes of this grouping, acetic acid and urea, are about
+    3 times faster than the slowest, acetone. %, but only about 10 \% smaller.
   \end{itemize}
@@
     \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
-  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
+  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity. % citation
   	\item Given their lower propensity to hydrogen bond one might expect amides to partition
   	out of the pore and/or to move through the pore quickly, perhaps faster than methanol.
-    \item The peaks in their radial density are still situated between the pore center and the
-    head groups, but closer to the pore center than other solutes that hydrogen bond with 
-    carboxylate groups (see Figure~\ref{fig:simple_alcohol_rdf}, for example).
+    \item Both RDFs contain peaks in their radial density that are situated between the 
+    pore center and the head groups, but closer to the pore center than other solutes that
+    hydrogen bond with carboxylate groups.
+    \item Solutes that hydrogen bond frequently tend to show peaks in their RDFs near 
+    0.5-0.6 nm from the pore center (see Figure~\ref{fig:simple_alcohol_rdf}, for example) 
+    and those that coordinate with sodium ions more frequently tend to show peaks in
+    their RDFs near 0.2-0.3 nm from the pore center.
     \item Both solutes spend about half of their time with their carbonyl oxygen atom 
     coordinated to a sodium ion which restrains the solutes to within the pore region
-    %BJC: it's possible the solutes hop from sodium to sodium quickly meaning solutes are not always immobilized.
-    %BJC: could look into lifetime of association
-    \item Interestingly, only the carbonyl oxygen atoms coordinate with sodium ions. 
-    The nitrogen atoms dooes not coordinate at all despite a similar negative partial
-    charge. The attached hydrogen atoms may shield this interaction.
-  \end{itemize}
-
-  \noindent Acetone has the lowest MSD of this set because it is primarily trapped near and behind 
-  the head groups.
+    \item Only the carbonyl oxygen atoms coordinate with sodium ions. 
+    The nitrogen atoms do not coordinate at all despite a similar negative partial
+    charge because the attached hydrogen atoms shield this interaction by making the
+    NH\textsubscript{2} group approximately neutral.
+  \end{itemize}
+
+  \noindent Acetone has the lowest MSD of this set because it either coordinates with
+  sodium or stays trapped near and behind the head groups.
   \begin{itemize}
     \item On average, acetone coordinates with sodium with the same frequency as acetic acid 
+    which is manifested as a peak in its RDF about 0.2 nm from the pore center.
     \item However, acetic acid spends more time in the pore center and therefore encounters
@@
   \caption{(a) The radial density near the pore center (r = 0) decreases
-  with decreasing solute MSD. (b) The amides hydrogen bond with water far
-  less than acetic acid, however they tend to coordinate with sodium ions
-  more frequently.}\label{fig:ketones}
+  with decreasing solute MSD. Peaks in the RDFs of urea, acetamide and
+  acetone near 0.2 - 0.3 nm from the pore center are likely due to coordination
+  with sodium ions. (b) The amides hydrogen bond with water far less than 
+  acetic acid, however they tend to coordinate with sodium ions more 
+  frequently.}\label{fig:ketones}
   \end{figure}
@@
   glycol and acetone.
-%  Finally, we studied the transport properties of sulfur-containing compounds similar
-%  to some of the solutes studied above.
   \begin{itemize}
     \item We replaced all but one oxygen atom of ethylene glycol and glycerol with sulfur atoms
-    to create Dimercaptoethanol and 2,3-Dimercapto-1-propanol.
+    to create dimercaptoethanol and 2,3-dimercapto-1-propanol.
     \item We replaced the carbonyl carbon of acetone with sulfur in order to create DMSO. 
-  	\item Sulfur is unable to hydrogen bond, however it is soluble in water  %BJC: maybe a reference to why sulfur can't hbond
- \end{itemize}
-
-%  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
-%  \end{itemize}
+  	\item Sulfur is unable to hydrogen bond making thiols less soluble in water than
+  	their hydroxyl group analogs.  % citation
+ \end{itemize}
 
@@
   \caption{(a) The RDF of mercaptoethanol is similar to ethylene glycol except 
-  for its higher density in the tail region. (b) 2,3-Dimercapto-1-propanol is
-  densest near the pore wall, unlike glycerol whose density is very high in the pore
-  center. (c) Dimethylsulfoxide has a higher density than acetone close to the pore
-  center which may in part explain its marginally larger MSD.}\label{fig:sulfur_analog_rdfs}
+  for its higher density in the tail region and consequently lower density in the
+  pore region. (b) 2,3-dimercapto-1-propanol is densest near the head groups, 
+  unlike glycerol whose density is very high close to the pore center. 
+  (c) Overall, dimethylsulfoxide has a higher density than acetone within the 
+  pore region which may in part explain its marginally larger MSD.}\label{fig:sulfur_analog_rdfs}
   \end{figure}
@@
     \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
-    \item This may lead to larger hops in the pore region.
+    which may lead to larger hops when in the pore region.
+    \item The range of behaviors shown by mercaptoethanol explain the large variance
+    of its MSD.
 %    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
@@
 
-  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
-  near monomer head groups. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
-  \begin{itemize}
-    \item Glycerol frequently hydrogen bonds with more than one head group at a time (See Figure~\ref{fig:multi_hbonds}).
-    % BJC: can probably quantify the following:
-    \item It can also hydrogen bond with water molecules which increases its stability
-    in the pore region.
-    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups 
-    so it gravitates towards the head group region.
+  \noindent 2,3-dimercapto-1-propanol exhibits slower transport than glycerol 
+  because more of it partitions into the tail region. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
+  \begin{itemize}
+    % BJC1: maybe next point better expressed as a percentage in each region.
+    \item The density of glycerol is always higher up to 0.7 nm from the 
+    pore center where the population of 2,3-dimercapto-1-propanol then 
+    becomes more dense into the tail region. 
+    \item Glycerol participates in about 3 times as many hydrogen bonds
+    as 2,3-dimercapto-1-propanol. %BJC1: 52.2 / 16.4 ~= 3.2. Includes hbonds with water (recieved and donated) as well as with ether + carboxylate oxygen atoms.
+    \item Because sulfur cannot hydrogen bond, 2,3-dimercapto-1-propanol is 
+    less soluble than glycerol in the water-filled pores and more readily 
+    partitions into the tail region.
   \end{itemize}
@@
   \begin{itemize}
-    \item The radial density of DMSO is higher than acetone close to the pore center.
+    \item The density of DMSO is higher than acetone in the pore region,
+    except for the peak exhibited by acetone near 0.2 nm, which is due to 
+    sodium ion association.
+    %BJC1: better to report a percentage?
+    \item On average, the 24 DMSO molecules coordinate with 8.4 sodium ions 
+    per frame, compared to 6.2 per frame by acetone.
   	\item The pyramidal structure of DMSO may force it to spend more time closer to
-  	the pore center.
-  	%BJC: quantify sodium coordination O group of DMSO
-  \end{itemize}
-
-  \subsection*{Hydrogen bond acceptors}  % Need a better heading since all molecules in this study are acceptors
-
-  %BJC: should probably at least mention acetone again in this section  
+  	the pore center which increases its interaction with sodium ions.
+  	\item The tendency of DMSO to stay in the pore region counterbalances the
+  	sodium ion interactions to give it a higher MSD than acetone. 
+  \end{itemize}
+
+  \subsection*{Hydrogen Bond Acceptors}  % Need a better heading since all molecules in this study are acceptors
+
+  % BJC: should probably at least mention acetone again in this section  
   The slowest set of molecules we studied can accept hydrogen bonds, but cannot donate
@@
   	\item The MSDs of ethyl acetate, propylene carbonate and acetone are only marginally larger.
-  	% EAC and PCB are both larger molecules. Acetone is small. %BJC: not sure how far I should dive into this point
   \end{itemize}
@@
 
-  \noindent The radial density of solutes near the pore center in this set is surprisingly high
-  as shown in Figure~\ref{fig:nondonors_rdf}.
+  \noindent The radial density of solutes near the pore center in this set is 
+  surprisingly high as shown in Figure~\ref{fig:nondonors_rdf}.
   \begin{itemize}
@@
     in this study. Their size prevents them from easily entering the tail 
-    region and generally gives faster transport properties since they spend
-    more time in the pore region. 
+    region and consequently gives faster transport properties 
+    % since they spend more time in the pore region. 
     \item However, this is not a hard rule. When a solute does overcome the 
     barrier of entry beyond the head group region, it can become trapped. All
-    solutes in this set show a peak $\geq$ 1 nm from the pore center which is
-    likely caused by solutes that get trapped in the tail region for a significant
-    amount of time.
-	\item The peak density of THF is considerably offset from the pore center.
-	\item Observations of single THF trajectories have revealed that it does not make
-	large hops while in the pore center.
-	\item THF becomes nearly immobilized while associated with sodium ions (See 
-	Figure~\ref{fig:thf_sodium_coordination}).
+    solutes in this set show at least a small peak $\geq$ 0.9 nm from the pore 
+    center which is likely caused by solutes that get trapped in the tail region
+    for a significant amount of time.
+  \end{itemize}
+
+  \noindent Solutes do not make frequent hops while in the pore region.
+  \begin{itemize}
+	\item Observations of single THF trajectories have revealed that it becomes 
+	nearly immobilized while associated with sodium ions 
+	(See Figure~\ref{fig:thf_sodium_coordination}).
 	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
@@
 
-  \noindent Carbonyl groups continue to show high degrees of association with sodium ions. 
+  \noindent Carbonyl groups continue to show high degrees of association with
+  sodium ions. 
   \begin{itemize}
@@
     contain nitrogen (see figure~\ref{fig:ketone_hbonds}).
-    \item In all cases, other polar groups on carbonyl-containing compounds
-    associate with sodium in negligible amounts.
-  \end{itemize}
-
-  \begin{figure}
+%    \item In all cases, other polar groups on carbonyl-containing compounds
+%    associate with sodium in negligible amounts.
+  \end{itemize}
+
+  \begin{figure}[!htb]
   \centering
@@
   \end{subfigure}
+  \caption{(a) The radial density of solutes that can only receive hydrogen bonds
+  is surprisingly high in the pore region. Conversely, there is also an appreciable
+  amount of each solute in the tails. (b) The low MSDs exhibited by each of these
+  solutes is due to a combination of entrapment within the tail region and a high 
+  degree of coordination with sodium ions.}\label{fig:nondonors}
   \end{figure}
@@
 
-  Since solutes move slowly well entangled among the monomer tails, one can try to
+  Since solutes move slowly while entangled among the monomer tails, one can try to
   design monomers that better control the partition of solutes between the pore and
@@
     \item We have observed a significant amount of sodium association with 
-    negatively charge solute constituents.
+    electronegative solute constituents.
     \item Changing the size and valence of the counter ion may offer some
@@
 
-  We learned that solutes undergo anomalous diffusion which can be described 
-  as a subordinated fractional brownian motion process. 
-  \begin{itemize}
-    \item In general, solutes hop intermittently between periods of entrapment
-    \item These hops are anti-correlated to their previous hops
-  \end{itemize}
+%  We learned that solutes undergo anomalous diffusion which can be described 
+%  as a subordinated fractional brownian motion process. 
+%  \begin{itemize}
+%    \item In general, solutes hop intermittently between periods of entrapment
+%    \item These hops are anti-correlated to their previous hops
+%  \end{itemize}
 

### 2019-03-20 Ben_Manuscripts/transport/figures/multi_hbonds.py

@@ -20,6 +20,7 @@ n_std = []
 start = 0
 
 fig, ax = plt.subplots(figsize=(7, 5))
+ax2 = ax.twinx()
 bar_width = 0.2
 opacity = 0.8
 loc = 0
@@ -34,7 +35,6 @@ for i in solutes:
     quadruple = 0
 
     sys = file_rw.load_object('%s/%s/10wt/hbonds.pl' % (path, i))
-    print(sys.t.n_frames)
     res_numbers = sys.number_residues(i)[0]
     for a in sys.hbonds:
         numbers = [res_numbers[j] for j in a[0]]
@@ -51,22 +51,27 @@ for i in solutes:
     double /= sys.t.n_frames
     triple /= sys.t.n_frames
     quadruple /= sys.t.n_frames
+    total = single + 2*double + 3*triple + 4*quadruple
 
     start_loc = loc
+
+    ax.bar(loc, total, bar_width, color='white', hatch='/', alpha=opacity, edgecolor='black', label='Total')
+    loc += bar_width
+
     if single != 0:
-        ax.bar(loc, single, bar_width, color='xkcd:blue', alpha=opacity)
-        loc += bar_width
+        ax2.bar(loc, single, bar_width, color='xkcd:blue', alpha=opacity)
+    loc += bar_width
     if double != 0:
-        ax.bar(loc, double, bar_width, color='xkcd:orange', alpha=opacity)
-        loc += bar_width
+        ax2.bar(loc, double, bar_width, color='xkcd:orange', alpha=opacity)
+    loc += bar_width
         #print(single / double)
     if triple > 0.1:
-        ax.bar(loc, triple, bar_width, color='xkcd:green', alpha=opacity)
-        loc += bar_width
+        ax2.bar(loc, triple, bar_width, color='xkcd:green', alpha=opacity)
+    loc += bar_width
         #print(double / triple)
     if quadruple > 0.1:
-        ax.bar(loc, quadruple, bar_width, color='xkcd:red', alpha=opacity)
-        loc += bar_width
+        ax2.bar(loc, quadruple, bar_width, color='xkcd:red', alpha=opacity)
+    loc += bar_width
         #print(triple / quadruple)
 
     xticks.append((-bar_width / 2) + start_loc + (loc - start_loc) / 2)
@@ -75,15 +80,18 @@ for i in solutes:
[…]

### 2019-03-25 Ben_Manuscripts/transport/Outline.tex
comments.
Figure and organization updates

@@
 %\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
-\title{Chemically Dependent Selectivity in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
 
+  %BJC2: Changed format from numbered questions to more of a roadmap for this paper
+
+  First, we will comment on the membrane's structure.
+  \begin{itemize}
+    \item We have previously studied dry membrane systems and some systems with
+    low water content.
+    \item We will observe how the radial density of monomer components and water
+    change based on membrane water content.
+  \end{itemize}
+
+  Then we will present our efforts to understand how small molecules, including water
+  partition within the pores?
+  \begin{itemize}
+    \item From a macroscopic perspective, it is straightforward to hypothesize that 
+    the water and polar solutes spend their time exclusively in the tube-like hydrophilic
+    pore region.
+    \item Our previous work showed that there is a gradual compositional transition 
+    from the hydrophilic to the hydrophobic region which means that solutes may not 
+    necessarily stay confined to the centers of the pores or even within the
+    pore region. 
+    \item We will study the gradient in composition of solutes and water and any 
+    resultant influence it might have on mechanistic properties.
+  \end{itemize}
+
+  Finally, and for the bulk of this work, we will present our observations and explantions
+  of the various transport mechanisms exhibited by water and solutes.
+  \begin{itemize}
+    \item Given that the pores will restrict motion of the solutes, we anticipate that 
+    transport will be hindered in some way. 
+    \item We want to understand the differences in solute motion, specifically its mean
+    squared displacement (MSD), based on a solute's size, shape and chemical functionality.
+    \item We will study the interactions between solutes, the membrane, and water in order
+    to determine which mechanism or mechanisms dominate.
+  \end{itemize}
+
 %  There are a number of questions that we wish to answer in order to create a
 %  framework for studying this system in even greater detail.
-  \noindent There are a number of questions we wish to address in order to characterize
-  transport in this system.
-  \begin{enumerate}
-
-   	\item What transport mechanisms do we observe? \label{question:mechanisms}
-
-  	Given that the pores will restrict motion of the solutes, we anticipate that 
-  	transport will be hindered in some way. We want to understand the differences in
-  	solute motion, specifically its mean squared displacement (MSD), based on a solute's
-  	size, shape and chemical functionality. We will study the interactions
-  	between solutes, the membrane, and water in order to determine which mechanism
-  	or mechanisms dominate.
-
-  	\item How do molecules, including water, partition within the pores? \label{question:partition}
-
-  	From a macroscopic perspective, it is straightforward to hypothesize that the water and
-  	polar solutes spend their time exclusively in the tube-like hydrophilic pore region.
-  	Our previous work showed that there is a gradual compositional transition from the 
-  	hydrophilic to the hydrophobic region which means that solutes may not 
-  	necessarily stay confined to the centers of the pores or even within the
-  	pore region. We will study the gradient in composition of solutes and water
-  	and any resultant influence it might have on mechanistic properties.
-
-%  	\item Can we describe the transport mechanisms using pre-existing 
-%  	mathematical models. \label{question:math}
-%  	
-%  	A mathematical model may provide additional insight into the transport
-%  	mechanisms and, in future work, can help relate performance on the 
-%  	timescales studied with MD to macroscopic timescales. We will use
-%  	qualitative and semi-quantitative arguments in order to choose a 
-%  	governing model.
-
-  	\item How can we modify the current monomers in order to enhance
-  	solute-specific separations? \label{question:math}
-
-  	Most experimental characterization up to this point has been centered 
-  	around the monomer, Na-GA3C11, studied here. The primary reason for conducting
-  	these simulations is to understand what chemical modifications can be made 
-  	to this or similar liquid crystal molecules in order to enhance transport 
-  	of desired species or restrict that of undesired species. We will use the 
-  	insight gained from our mechanistic observations in order to suggest new 
-  	monomer designs.
-
-  \end{enumerate}
+%  \noindent There are a number of questions we wish to address in order to characterize
+%  transport in this system.
+%  \begin{enumerate}
+%  
+%   	\item What transport mechanisms do we observe? \label{question:mechanisms}
+%  	
+%  	Given that the pores will restrict motion of the solutes, we anticipate that 
+%  	transport will be hindered in some way. We want to understand the differences in
+%  	solute motion, specifically its mean squared displacement (MSD), based on a solute's
+%  	size, shape and chemical functionality. We will study the interactions
+%  	between solutes, the membrane, and water in order to determine which mechanism
+%  	or mechanisms dominate.
+%  
+%  	\item How do molecules, including water, partition within the pores? \label{question:partition}
+%  	
+%  	From a macroscopic perspective, it is straightforward to hypothesize that the water and
+%  	polar solutes spend their time exclusively in the tube-like hydrophilic pore region.
+%  	Our previous work showed that there is a gradual compositional transition from the 
+%  	hydrophilic to the hydrophobic region which means that solutes may not 
+%  	necessarily stay confined to the centers of the pores or even within the
+%  	pore region. We will study the gradient in composition of solutes and water
+%  	and any resultant influence it might have on mechanistic properties.
+%  	
+%%  	\item Can we describe the transport mechanisms using pre-existing 
+%%  	mathematical models. \label{question:math}
+%%  	
+%%  	A mathematical model may provide additional insight into the transport
+%%  	mechanisms and, in future work, can help relate performance on the 
+%%  	timescales studied with MD to macroscopic timescales. We will use
+%%  	qualitative and semi-quantitative arguments in order to choose a 
+%%  	governing model. 
+%  	
+%        %MRS2: this is beyond the scope of what we can really answer. We can hypothesize things, but 
+%        % we really haven't really done any experiments to confirm these.  So this should be deemphasized.
+%  	\item How can we modify the current monomers in order to enhance
+%  	solute-specific separations? \label{question:math}
+%  	
+%  	Most experimental characterization up to this point has been centered 
+%  	around the monomer, Na-GA3C11, studied here. The primary reason for conducting
+%  	these simulations is to understand what chemical modifications can be made 
+%  	to this or similar liquid crystal molecules in order to enhance transport 
+%  	of desired species or restrict that of undesired species. We will use the 
+%  	insight gained from our mechanistic observations in order to suggest new 
+%  	monomer designs.
+%  	
+%  \end{enumerate}
 
@@
   %BJC: or should that go in the main body results?
+  %MRS2: depends on whether it's necessary to support the main hypothesis. 
+  %BJC2: made more vague and included specifics in membrane structure section
   We observed that water partitions into the tail region of our system and therefore
@@
   \begin{itemize}
-	\item There is a 2:1 ratio of water in the pores versus in the tails for the 10 wt \% system.
+    \item We define the partition between the pore and tail region to be ca. 1.5 nm from
+    the pore center based on the minimum in the radial distribution of water (See section~\ref{method:rdfs}).
+%	\item There is a 2:1 ratio of water in the pores versus in the tails for the 10 wt \% system.
 	\item The amount of water present in the tails may or may not be experimentally consistent
@@
 	will give issues with measurements and calculations.
-	\item See section~\ref{S-section:water_content_equil} of the SI for further details on 
-	water equilibration in this system.
+%	\item See section~\ref{S-section:water_content_equil} of the SI for further details on 
+%	water equilibration in this system.
 	\item We iteratively adjusted the pore radius in our systems until the right amount of water
@@
 	with short energy minimizations between insertions.
+	\item When studying transport of water in the pores, we limited the calculations
+	to water molecules that spend greater than 95 \% of their time in the pore region.
   \end{itemize}
@@
     % MRS1: time vs. ensemble MSD better in follow-up paper.
+    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
+    % fully understand the theory since I talk about subdiffusion in terms of 
+    % alpha which is always calculated based on ensemble MSD unless we know for sure that
+    % the system is ergodic (which it isn't the case for CTRW)
 	\item In practice, $\alpha$ corresponds to the growth of the \textit{ensemble}
@@
   a 2.5 ns simulation of solutes dissolved in a cubic box of water.
+  % MRS2: this might be slightly larger than the hydrodynamic radius?  We might not be able to place it 
+  % directly into stoke-einstein.
+  % BJC2: Yeah, I've thought about this. Actually calculating the hydrodynamic
+  % radius would involve a viscosity calculation (which I have the tools to do)
   \begin{itemize}
@@
 
-  \subsection*{Radial Density Functions}\label{method:rdfs}
-  % BJC1: Should it be Radial Distribution Functions?
+  \subsection*{Radial Distribution Functions}\label{method:rdfs}
 
@@
   %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
+  %BJC2: sensitivity added to supporting information
   %we are not picking and choosing results (either consciously or unconsciously) 
@@
 
-  %BJC: Do analysis on pure water system for this section.
+  %TODO redo analysis on pure water system for this section.
 
@@
 
-  % BJC1: Should I show a dry system?
   \begin{figure}[!htb]
@@
   \end{subfigure}
-
   %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
   %BJC1: tried it out. Seems like a good addition.
+  %MRS2: I wonder to what extent it would help to show the curves on top of each other to make it clear
+  %how much things are displaced.
+  %BJC2: I'll see what I can do without overly cluttering the figure
   \caption{The radial densities of various monomer components paint a picture of the
@@
 
+  There is an appreciable amount of water that partitions into the tail region of both
+  systems.
+  \begin{itemize}
+    \item 28 \% and 31 \% of the total water is present in the tail regions of the 5 and 
+    10 wt\% water systems respectively 
+    \item See section~\ref{S-section:water_content_equil} of the SI for more details.
+    \item This result is likely due to a combination of the lower density of the tail region
+    and oxygen atoms at the ends of each monomer tail which can stabilize water molecules. %TODO Total density as function of distance from pore center.
+  \end{itemize}
+
   \subsection*{Mechanisms Governing Small Solute Transport}\label{section:mechanism_overview}
@@
     molecules in the 5 wt\% system.
-    \item The low levels of water coordination under confinement are likely driven
-    in part by favorable interactions between sodium ions and carboxylate head groups.
-    \item A dehydrated sodium ion is not well shielded from the negatively charged 
-    carboxylate group.~\cite{ma_drastically_2019}. 
+    \item However, the sodium ions are not undercoordinated since they frequently 
+    pair with carboxylate head groups.
+    %MRS2: might need to point out that they are not that undercoordinated, as they also coordinate with solutes.
+    %BJC2: not solutes here, because the final calculations will be done for a pure water system.
+%    \item The low levels of coordination with water under confinement are likely driven
+%    in part by favorable interactions between sodium ions and carboxylate head groups.
+%    \item A dehydrated sodium ion is not well shielded from the negatively charged 
+%    carboxylate group.~\cite{ma_drastically_2019}. 
     \item On average, sodium ions coordinate with 0.5 carboxylate group oxygen atoms in the
@@
   \end{subfigure}
-  %BJC: missing a few since those simulations just got started
   %BJC1: wondering if I should add some kind of confidence interval to the Stoke-Einstein plots. Based on the errorbars of methanol
+  %MRS2: probably, perhaps as a colored background.  But might make it too noisy to read.  MAybe color them by chemical group?
   %BJC1: should the points be labeled with residue names?
+  %MRS2: as long as there is a table in SI with the relevant information, probably isn't needed.  That would also make it hard to read the plot.   
+  %MRS2: for the plots with fewer points (like alcohol), the individual points should be labeled, there is room.
+  %MRS2: as discussed, maybe for each solute group, have a MSD plot a) and RDF plt b) and other important plots in c) and d)
   \begin{subfigure}{0.45\textwidth}
@@
   \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
-  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
   \begin{itemize}  
@@
     least a short period of time. 
-    \item There are some cases where solutes become immobilized for long periods
-    of time while in close proximity to a sodium ion.
-    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
-    within 2.5 \AA~of a sodium ion for the entire length of a trapping occurence.
-  \end{itemize}
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
-  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
-  the majority of the trapping occurence between 400 and 600 ns. Regions
-  highlighted red or blue indicate times when methanol's oxygen atom is within 
-  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
-  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
-  \end{figure}
+    \item Some kind of pair time distribution  %TODO
+%    \item There are some cases where solutes become immobilized for long periods
+%    of time while in close proximity to a sodium ion.
+%    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
+%    within 2.5 \AA~of a sodium ion for the entire length of a trapping occurence.
+  \end{itemize}
+
+  % BJC2: moved to supporting since anecdotal
+%  \begin{figure}[!htb]
+%  \centering
+%  %MRS2: would be better if this was paired with ensemble data, instead of just one trajectory.
+%  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
+%  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
+%  the majority of the trapping occurence between 400 and 600 ns. Regions
+%  highlighted red or blue indicate times when methanol's oxygen atom is within 
+%  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
+%  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
+%  \end{figure}
 
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
-  % BJC: This might be better cut off at y ~ 0.6 and then provide an inset with full RDFs
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\linewidth]{msd_radius_diols_10wt.pdf}
+  \caption{}\label{fig:polyols_rdf}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\linewidth]{polyols_rdf.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.50\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \vspace{-0.275cm}
@@
 %  \end{subfigure}
+%MRS2: maybe include the MSD vs size plot subset here. 
   \caption{(a) Glycerol, tetrose and ribose are densest close to the pore center because
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{msd_radius_ketones_10wt.pdf}
+  \caption{}\label{fig:ketones_rdf}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{ketone_rdf.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{ketone_hbonds.pdf}
@@
   \centering
-  \begin{subfigure}{0.325\linewidth}
+  \begin{subfigure}{0.45\linewidth}
+  \includegraphics[width=\textwidth]{msd_radius_sulfur_10wt.pdf}
+  \caption{}\label{fig:SOH_GCL_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.45\linewidth}
   \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\linewidth}
+  \begin{subfigure}{0.45\linewidth}
   \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\linewidth}
+  \begin{subfigure}{0.45\linewidth}
   \includegraphics[width=\textwidth]{thiol_comparison_DMS.pdf}
@@
     glycol molecules beyond 0.8 nm from the pore center. 
-    \item Conversely, mercaptoethanol exhibits some of the highest single solute MSDs 
-    (See Figure~\ref{fig:SOH_trace})  % Only methanol has greater (I think)
+%    \item Conversely, mercaptoethanol exhibits some of the highest single solute MSDs 
+%    (See Figure~\ref{fig:SOH_trace})  % Only methanol has greater (I think)
     \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
@@
     of its MSD.
+    \item Average hop length while in pore region maybe %TODO
 %    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
@@
 
-  %BJC: Could be a supporting figure
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{SOH_trace.pdf}
-  \caption{}\label{fig:SOH_trace}
-  \end{subfigure}
-  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
-  to lengthy trapping. Large hops generally occur near the pore center while 
-  long entrapments occur while tangled among the monomer tails.}
-  \end{figure}
+  %BJC2: Moved to supporting figure since anecdotal
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{SOH_trace.pdf}
+%  \caption{}\label{fig:SOH_trace}
+%  \end{subfigure}
+%  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
+%  to lengthy trapping. Large hops generally occur near the pore center while 
+%  long entrapments occur while tangled among the monomer tails.}
+%  \end{figure}
 
@@
     %BJC1: better to report a percentage?  
-    \item On average, the 24 DMSO molecules coordinate with 8.4 sodium ions 
-    per frame, compared to 6.2 per frame by acetone.
+    %MRS2: yes, report as intensive quantity
+    \item On average, 35 \% of DMSO molecules are coordinated to a sodium ion each
+    frame compared with 26 \% of acetone molecules.
+%    \item On average, the 24 DMSO molecules coordinate with 8.4 sodium ions 
+%    per frame, compared to 6.2 per frame by acetone.
   	\item The pyramidal structure of DMSO may force it to spend more time closer to
@@
   \noindent Solutes do not make frequent hops while in the pore region.
-  \begin{itemize}
-	\item Observations of single THF trajectories have revealed that it becomes 
-	nearly immobilized while associated with sodium ions 
-	(See Figure~\ref{fig:thf_sodium_coordination}).
+  %MRS2: is this because you need H-bonding to make hops? We should have some sense of this.
+  \begin{itemize}
+%	\item Observations of single THF trajectories have revealed that it becomes 
+%	nearly immobilized while associated with sodium ions 
+%	(See Figure~\ref{fig:thf_sodium_coordination}).
 	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{msd_radius_nondonors_10wt.pdf}
+  \caption{}\label{fig:nondonors_rdf}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{nondonors_rdf.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{nondonor_hbonds.pdf}
@@
 
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
-  %BJC: figure was hard to make exactly how I wanted it so I stopped until we decide the best way to illustrate this point
-  %BJC: Should I do two colorbars (one for sodium, one for THF)
-  %BJC: Should Sodium-THF distance be between THF COM and sodium in order to be consistent with above figure? 
-  \caption{Coordination of THF with sodium ions may help stabilize it inside the
-  pore region. For the first 700 ns of the trajectories shown, the center of mass
-  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
-  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
-  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
-  After 700 ns, THF separates from the sodium ion and moves closer to the head group
-  region.}\label{fig:thf_sodium_coordination}
-  \end{figure}
-
+  %BJC2: moved to supporting information
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
+%  %BJC: figure was hard to make exactly how I wanted it so I stopped until we decide the best way to illustrate this point
+%  %BJC: Should I do two colorbars (one for sodium, one for THF)
+%  %BJC: Should Sodium-THF distance be between THF COM and sodium in order to be consistent with above figure? 
+%  \caption{Coordination of THF with sodium ions may help stabilize it inside the
+%  pore region. For the first 700 ns of the trajectories shown, the center of mass
+%  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
+%  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
+%  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
+%  After 700 ns, THF separates from the sodium ion and moves closer to the head group
+%  region.}\label{fig:thf_sodium_coordination}
+%  \end{figure}
+  %MRS2: Can we show something that describes a distribution of multiple THF? this is just one, 
+  % which is suggestive, but this sort of suggestive information maybe should be in supporting. 
+  %MRS2: did you trace down any information on THF-ion complexation? We should be able to report on whether
+  %this is physical or a force field artifact.
+  % BJC2: probably better to find evidence of ether-ion complexation since it applies to multiple
+  % solutes that we studied
   % THF shows highly anticorrelated hops
@@
   %All have comparable densities near pore center except acetone which is lower
-
-  \subsection{Design Considerations}
-
-  Based on our observations of the complex interactions between various polar solutes
-  and the membrane's liquid crystal monomers, we can speculate on design criteria for 
-  the next generation of liquid crystal monomers to be used for LLC membrane
-  synthesis.
-  \begin{itemize}
-    \item Unfortunately, we cannot comment on the stability of the H\textsubscript{II}
-    phase if major changes are made to the monomers.
-    \item Therefore, our most feasible design suggestions are those which can be made
-    as a post-processing step to the cross-linked membrane created using Na-GA3C11.
-  \end{itemize}
-
-  The transport properties of solutes are a strong function of the 3 trapping
-  mechanisms discussed above. Therefore, it is most logical to design monomers with 
-  them in mind.
-
-  Since solutes move slowly while entangled among the monomer tails, one can try to
-  design monomers that better control the partition of solutes between the pore and
-  tail region.
-  \begin{itemize}
-    \item The head groups of Na-GA3C11 are planar which leaves a fair amount of space
-    between adjacent head groups and it makes it easier for solutes to slip between and
-    past them.
-    \item Bulkier substituents, which do not impede stacking of monomers into columns,
-    might slow the rate at which solutes partition into the tails.
-    \item Additionally, one can include crosslinkable groups near the head groups in
-    order to fill free volume and effectively create a wall.
-    \item Finally, removal of the ether linkages between the head groups and the monomer
-    tails will decrease the stability of polar molecules in the head group region.
-    \item Overall, controlling the solute partition might not be the most important 
-    consideration to optimize because once enough solutes flow through, the membrane tail
-    region will become saturated with solute molecules and greatly reduce the rate of partition.
-  \end{itemize}
-
-  Alternatively, one can focus on designing head groups with varying hydrogen 
-  bonding capabilites.
-  \begin{itemize}
-    \item Na-GA3C11 has a carboxylate group which readily accepts hydrogen bonds
-    \item One can increase the number of hydrogen bonding sites on the head groups
-    in order to trap more solutes, or decrease the number of hydrogen bond sites
-    to trap less.
-  \end{itemize}
-
-  Finally, one can attempt to control the degree to which solutes coordinate 
-  with counterions.
-  \begin{itemize}
-    \item We have observed a significant amount of sodium association with 
-    electronegative solute constituents.
-    \item Changing the size and valence of the counter ion may offer some
-    interesting behavior. 
-    \item For example, a counter ion with a charge of +2 may attract more solute
-    molecules and bind them more tightly, but there will only be half as many
-    counterions in the system which may reduce its overall influence.
-    \item Additionally, the size of the counterion will affect the mobility
-    of any complex formed. 
-    \item Sodium appears to do a good job of immobilizing complexes formed between
-    it and solutes. 
-    \item However, a Lithium ion might be more prone to go along for the ride.
-    \item Hydrogen would likely spend the majority of its time bound to the 
-    carboxylate head group or as part of a hydronium ion hence interfering with 
-    solute transport infrequently.
-  \end{itemize}
+%
+%  \subsection{Design Considerations}
+
+  %MRS2: should be a bit careful on what WILL happen, as opposed to what might happen.
+  %BJC2: condensed and added to conclusions.
+
+%  Based on our observations of the complex interactions between various polar solutes
+%  and the membrane's liquid crystal monomers, we can speculate on design criteria for 
+%  the next generation of liquid crystal monomers to be used for LLC membrane
+%  synthesis.
+%  \begin{itemize}
+%    \item Unfortunately, we cannot comment on the stability of the H\textsubscript{II}
+%    phase if major changes are made to the monomers.
+%    \item Therefore, our most feasible design suggestions are those which can be made
+%    as a post-processing step to the cross-linked membrane created using Na-GA3C11.
+%  \end{itemize}
+%  
+%  The transport properties of solutes are a strong function of the 3 trapping
+%  mechanisms discussed above. Therefore, it is most logical to design monomers with 
+%  them in mind. 
+%  
+%  Since solutes move slowly while entangled among the monomer tails, one can try to
+%  design monomers that better control the partition of solutes between the pore and
+%  tail region.
+%  \begin{itemize}
+%    \item The head groups of Na-GA3C11 are planar which leaves a fair amount of space
+%    between adjacent head groups and it makes it easier for solutes to slip between and
+%    past them.
+%    \item Bulkier substituents, which do not impede stacking of monomers into columns,
+%    might slow the rate at which solutes partition into the tails.
+%    \item Additionally, one can include crosslinkable groups near the head groups in
+%    order to fill free volume and effectively create a wall.
+%    \item Finally, removal of the ether linkages between the head groups and the monomer
+%    tails will decrease the stability of polar molecules in the head group region.
+%    \item Overall, controlling the solute partition might not be the most important 
+%    consideration to optimize because once enough solutes flow through, the membrane tail
+%    region will become saturated with solute molecules and greatly reduce the rate of partition.
+%  \end{itemize}
+%  
+%  Alternatively, one can focus on designing head groups with varying hydrogen 
+%  bonding capabilites.
+%  \begin{itemize}
+%    \item Na-GA3C11 has a carboxylate group which readily accepts hydrogen bonds
+%    \item One can increase the number of hydrogen bonding sites on the head groups
+%    in order to trap more solutes, or decrease the number of hydrogen bond sites
+%    to trap less.
+%  \end{itemize}
+%  
+%  Finally, one can attempt to control the degree to which solutes coordinate 
+%  with counterions.
+%  \begin{itemize}
+%    \item We have observed a significant amount of sodium association with 
+%    electronegative solute constituents.
+%    \item Changing the size and valence of the counter ion may offer some
+%    interesting behavior. 
+%    \item For example, a counter ion with a charge of +2 may attract more solute
+%    molecules and bind them more tightly, but there will only be half as many
+%    counterions in the system which may reduce its overall influence.
+%    \item Additionally, the size of the counterion will affect the mobility
+%    of any complex formed. 
+%    \item Sodium appears to do a good job of immobilizing complexes formed between
+%    it and solutes. 
+%    \item However, a Lithium ion might be more prone to go along for the ride.
+%    %MRS2: hydrogen isn't a counter ion in and of itself, since it's only available either as hydronium 
+%    % or will protonate the head groups.
+%    \item Hydrogen would likely spend the majority of its time bound to the 
+%    carboxylate head group or as part of a hydronium ion hence interfering with 
+%    solute transport infrequently.
+%  \end{itemize}
 
@@
 
-  The MSD of solutes may be much larger in more concentrated solutions because there
-  will be less available trapping sites for them to occupy.
-  \begin{itemize}
-    \item We purposely studied the behavior of the solutes in dilute conditions.
-    \item The difference in size between water and the fastest solute, methanol, is not
-    enough to explain the order of magnitude difference in their average MSDs.
-    \item The sheer number of water molecules prevents the majority of them from 
-    becoming trapped for long periods of time.
-    \item A similar effect may increase solute MSDs in more concentrated solutions.
-  \end{itemize}
-
-  As a final consideration, water content affects pore size and strongly influences
-  the MSDs of solutes, water and counterions.
-  \begin{itemize}
-    \item The MSD of these components is about 2 orders of magnitude larger in the 
-    10 wt \% system than the 5 wt \% system.
-    \item The 5 wt \% system is much less feasible as a separations membrane on the basis
-    of water permeability alone.
-    \item Typically, the total water content used to create the H\textsubscript{II} phase
-    is reported, but the amount of water that resides in the pores, tails and in between
-    hexagonal mesophases is less clear.
-    \item Experiments, such as those by Jenkins et al.~\cite{jenkins_identification_2012}, 
-    may help elucidate the water composition in each region.
-    \item The results would be extremely useful for determining the viability of a given
-    LLC membrane system. 
-  \end{itemize}
+  %BJC2: will just leave out concentration dependence since the following is purely speculative
+  % and its one of the things I explicity said we would not address.
+%  The MSD of solutes may be much larger in more concentrated solutions because there
+%  will be less available trapping sites for them to occupy.
+%  %MRS2: but will there be more crowding?  Will depend on the equilibrium concentration 
+%  %of the different components in the pore, I suppose.  
+%  %MRS2: we may need to test this at some point, but it also would involve trying to figure out what the 
+%  %equilibrium concentration inside the pores was.
+%  \begin{itemize}
+%    \item We purposely studied the behavior of the solutes in dilute conditions.
+%    \item The difference in size between water and the fastest solute, methanol, is not
+%    enough to explain the order of magnitude difference in their average MSDs.
+%    \item The sheer number of water molecules prevents the majority of them from 
+%    becoming trapped for long periods of time.
+%    %MRS2: majority of the solutes?
+%    \item A similar effect may increase solute MSDs in more concentrated solutions.
+%  \end{itemize}
+
+%  As a final consideration, water content affects pore size and strongly influences
+%  the MSDs of solutes, water and counterions.
+%  \begin{itemize}
+%    \item The MSD of these components is about 2 orders of magnitude larger in the 
+%    10 wt \% system than the 5 wt \% system.
+%    \item The 5 wt \% system is much less feasible as a separations membrane on the basis
+%    of water permeability alone.
+%    \item Typically, the total water content used to create the H\textsubscript{II} phase
+%    is reported, but the amount of water that resides in the pores, tails and in between
+%    hexagonal mesophases is less clear.
+%    \item Experiments, such as those by Jenkins et al.~\cite{jenkins_identification_2012}, 
+%    may help elucidate the water composition in each region.
+%    \item The results would be extremely useful for determining the viability of a given
+%    LLC membrane system. 
+%  \end{itemize}
 
@@
   \begin{itemize}    
+    \item The MSD of these components is about 2 orders of magnitude larger in the 
+    10 wt \% system than the 5 wt \% system.
     \item As more water is added to the system, the pores become less crowded
-    with monomer components and the MSD of water, sodium and solutes increase.
+    with monomer components % and the MSD of water, sodium and solutes increase.
     \item The amount of water in the pores deserves special attention when 
@@
   \begin{itemize}
-    \item A solute can become stuck in the tail region. 
-    \item A solute can hydrogen bond with monomers
-    \item A solute can associate with a bound counterion
-  \end{itemize}
-
-  Based on these trapping mechanisms, we have suggested modifications that
+    \item A solute can become stuck among monomer tails. 
+    \item A solute can donate hydrogen bonds to monomers.
+    \item A solute can associate with a bound counterion.
+  \end{itemize}
+
+  % MRS2: recommendations are less important, as they are hypothetical. 
+  % BJC2: condensed above section so that this is the only discussion of possible modifications.
+  % BJC2: seems worth mentioning to make clear the value of our work.
+  Based on these trapping mechanisms, we can suggest modifications that
   can be made to monomers in order to mitigate or enhance their effect on
   solute MSDs.
+  \begin{itemize}
+    \item Since solutes move slowly while entangled among the monomer tails, one can try to
+    design monomers that better control the partition of solutes between the pore and
+    tail region.
+    \item For example, removal of the ether linkages between the head groups and the 
+    monomer tails will decrease the stability of polar molecules near the head groups.
+    \item Alternatively, one can focus on designing head groups with varying hydrogen 
+    bonding capabilities.
+    \item One can increase the number of hydrogen bonding sites on the head groups
+    in order to trap more solutes, or decrease the number of hydrogen bond sites
+    to trap less.
+    \item Finally, one can attempt to control the degree to which solutes coordinate 
+    with counterions.
+    \item Changing the size and valence of the counter ion may offer some
+    interesting behavior. 
+  \end{itemize}
 

### 2019-03-25 Ben_Manuscripts/transport/Supporting_Information.tex
Figure and organization updates

@@
 
-  \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensisitivity}
+  \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}
 
@@
   \end{figure}
+
+  \subsection{Solute Pairing with Sodium}
+
+  \begin{figure}[!htb]
+  \centering
+  %MRS2: would be better if this was paired with ensemble data, instead of just one trajectory.
+  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
+  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
+  the majority of the trapping occurence between 400 and 600 ns. Regions
+  highlighted red or blue indicate times when methanol's oxygen atom is within 
+  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
+  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
+  \end{figure}
+
+  %BJC: could probably safely remove this figure
+  \subsection{Mercaptoethanol's range of behavior}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{SOH_trace.pdf}
+  \caption{}\label{fig:SOH_trace}
+  \end{subfigure}
+  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
+  to lengthy trapping. Large hops generally occur near the pore center while 
+  long entrapments occur while tangled among the monomer tails.}
+  \end{figure}
+
+  \subsection{THF-sodium Complexation}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
+  \caption{Coordination of THF with sodium ions may help stabilize it inside the
+  pore region. For the first 700 ns of the trajectories shown, the center of mass
+  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
+  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
+  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
+  After 700 ns, THF separates from the sodium ion and moves closer to the head group
+  region.}\label{fig:thf_sodium_coordination}
+  \end{figure}
+  %MRS2: Can we show something that describes a distribution of multiple THF? this is just one, 
+  % which is suggestive, but this sort of suggestive information maybe should be in supporting. 
+  %MRS2: did you trace down any information on THF-ion complexation? We should be able to report on whether
+  %this is physical or a force field artifact.
+  % BJC2: probably better to find evidence of ether-ion complexation since it applies to multiple
+  % solutes that we studied
 

### 2019-04-01 Ben_Manuscripts/transport/Supporting_Information.tex
Updated outline

@@
 
-  \subsection{Solute Interaction}\label{section:solute_interaction}
+  \section{Solute Interaction}\label{section:solute_interaction}
 
@@
 
-  \subsection{Pore Splines}\label{section:splines}
+%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{section:se_sensitivity}
+%  
+%  In the main text, we estimated the trend in solute MSDs using the Stokes-Einstein
+%  equation with the correction factor of Gierer and Wirtz, $f$, given by 
+%  equation~\ref{M-eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
+%  
+%  We assumed that the Stokes-Einstein relationship could be approximated as a
+%  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
+%  by equation~\ref{M-eqn:correction_factor} of the main text, is only applied below
+%  a critical radius. At radii greater than the critical radius, $f$ = 1.
+%  
+%  In the main text, we constrained the corrected Stokes-Einstein equation so that
+%  it passed through the highest MSD value. We also plotted the uncorrected 
+%  Stokes-Einstein equation ($f$=1) as a lower bound to our expectations for 
+%  unrestricted solute motion. The lower bound is relatively insensitive to our
+%  choice of critical radius. Even for an unrealistically small critical radius 
+%  of 0.5 nm, the curve is within
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{stokes_intersection_sensitivity.pdf}
+%  \caption{We varied the molecular radius at which we assumed the Stokes-Einstein
+%  (SE) relationship to breaks down. It is assumed that the Gierer and Wirtz correction
+%  to the SE equation becomes a more accurate estimation of MSD at small radii, after
+%  the point of intersection }\label{fig:se_intersection_sensitivity}
+%  \end{figure}
+
+  \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}
+
+  We chose to report the MSD of our solutes after a 400 ns time lag. This choice does
+  not have a significant influence on the ranking of the solute MSDs. Although there
+  is minor re-ranking among solutes with similar MSDs, it does not affect any of 
+  the conclusions drawn in the main text.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_2.pdf}
+  \caption{Time lag = 200 ns}\label{fig:F0.2}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_3.pdf}
+  \caption{Time lag = 300 ns}\label{fig:F0.3}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_4.pdf}
+  \caption{Time lag = 400 ns}\label{fig:F0.4}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_5.pdf}
+  \caption{Time lag = 500 ns}\label{fig:F0.5}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_6.pdf}
+  \caption{Time lag = 600 ns}\label{fig:F0.6}
+  \end{subfigure}
+  \caption{The choice of time lag used to report solute MSDs does not 
+  influence the trends reported in the main text. We observe minor re-ranking
+  of solutes with similar MSDs and note that longer time lags generally
+  lead to large error bars on the MSDs, as expected. }\label{fig:lag_sensitivity}
+  \end{figure}
+
+  \section{Pore Splines}\label{section:splines}
 
@@
 
-  \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}
+  \section{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}
 
@@
 
-  \subsection{Solute Pairing with Sodium}
+  \section{Total Membrane Density}\label{section:total_density}
+
+  In our simulations, we observe that water partitions into the tail region
+  because of the tails' low density. We plotted the density of all atoms in 
+  the system as function of their $xy$ positions within the unit cell. The 
+  pore centers of the 5 and 10 wt \% water systems have a relatively low density
+  that is comparable to the density in the tails far from the pore center
+  (see figures~\ref{fig:total_density_5wt} and~\ref{fig:total_density_10wt}).
+  The density is highest near the middle of the tails. The observed density distribution
+  is necessary in order for the wedge-shaped monomers to fill space and stay in
+  the hexagonal phase. Accordingly, water is densest in the pore center and at 
+  the tail ends (see figures~\ref{fig:total_water_density_5wt} 
+  and~\ref{fig:total_water_density_10wt}). Very little water is present in the 
+  dense mid-tail region.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
+  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
+  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
+  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
+  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
+  \end{subfigure}
+  \caption{The lowest density regions of both membranes are in the pore center and in the
+  tail region, furthest from the pore center (a \& c). Water is densest in the low density
+  regions (b \& d).}\label{fig:total_density}
+  \end{figure}
+
+  \section{Solute Pairing with Sodium}
 
@@
   %BJC: could probably safely remove this figure
-  \subsection{Mercaptoethanol's range of behavior}
+  \section{Mercaptoethanol's range of behavior}
 
@@
 
-  \subsection{THF-sodium Complexation}
+  \section{THF-sodium Complexation}
 

### 2019-04-09 Ben_Manuscripts/transport/Draft.tex
Added draft

\documentclass[journal=jpcbfk,manuscript=article]{achemso}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{tcolorbox}
\usepackage{multicol}

\SectionNumbersOn

\externaldocument[S-]{Supporting_Information}

\title{Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

\begin{document}

  \graphicspath{{./figures/}}

  \begin{abstract}

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  for selective separations. In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We found
  that the transport rate of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. In general, we 
  observed that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

  \end{abstract}

  \section{Introduction}

  Membranes capable of separating nm-sized solutes with high selectivity 
  and permeability are highly desirable for a number of applications. For 
  example, separation of salt from seawater or other briny sources can 
  yield potable drinking water.\cite{fritzmann_state---art_2007} Removal
  of organic micropollutants, such as personal care products, pesticides
  and pharmaceuticals, from surface and groundwaters, can have large benefits
  for public health.\cite{schwarzenbach_challenge_2006} Finally,
  one can purify and recover dissolved species present in complex
  hydraulic fracturing flowback water waste streams which would help mitigate
  the effects of deep well injection and generate value.\cite{dischinger_application_2017} 
  %BJC: could make last point more general

%  All of these separations are possible with current commercial membrane
%  separation techniques but they are too energy intensive to be worth the 
%  capital investment needed to start the processes  
  All of these separations are possible with current commercial membrane
  separation techniques but suffer from serious drawbacks. Currently, reverse 
  osmosis (RO) and nanofiltration (NF) dominate commercial membrane separations
  of small molecules.\cite{warsinger_review_2018} RO membranes are typically
  dense polymer matrices that separate solutes based on differences in their
  solubility and permeability in the membrane material.\cite{fritzmann_state---art_2007}
  Although they can perform highly selective separations, high feed pressures,
  and thus large amounts of energy, are necessary in order to generate a 
  useful permeate flux.\cite{van_der_bruggen_review_2003} NF membranes have 
  well-defined nm-sized pores which can give the same permeate flux as RO
  with lower applied pressure.\cite{hilal_comprehensive_2004} However, the 
  pores are not uniform in size, limiting selectivity.\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

%  A membrane with the
%  selectivity of an RO membrane and the permeability of an NF membrane would
%  offer a significant improvement to current commercial membrane technology.
%  Nanostructured membranes offer the potential for molecular-level design 
%  which could overcome the limitations faced by conventional membrane 
%  technologies. One can create dense arrays of well-defined uniform-sized
%  \begin{itemize}
%    \item Mitigation of stochastic aspects of membrane synthesis
%    \item Well-defined and uniform pores increase selectivity
%    \item Solute-specific separations.
%  \end{itemize}

  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membranes are nanostructured membranes that may be able to achieve the
  selectivity of RO membranes while maintaining the high permeability
  of NF membranes.\cite{zhou_supported_2005} The H\textsubscript{II} LLC
  phase is formed when LLC monomers self-assemble into hexagonally packed
  and uniform-sized pores.\cite{smith_ordered_1997} Alignment and subsequent
  cross-linking of the hexagonal mesophases yields a mechanically strong
  membrane.\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
  enforce a strict molecular-size cut-off while the hexagonal geometry is 
  ideal for high permeability.\cite{zhou_supported_2005} Additionally, 
  because the LLC monomers are salts, Donnan exclusion plays a role in 
  rejection of charged molecules upon pore entry.\cite{donnan_theory_1995}
%  Zhou et al. demonstrated complete rejection
%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
%  membranes.\cite{zhou_supported_2005}

  In addition to geometric factors which make H\textsubscript{II} membranes
  ideal for selective separations, they have the potential to further disrupt
  conventional membrane separation techniques by being selective based not
  only on solute size and charge, but on chemical functionality as well. 
  The functional LLC monomer head groups that occupy the pore region of the
  membrane can interact with solutes. Dischinger et al. studied the 
  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
  similar pore topology to the H\textsubscript{II} phase, but a more 
  tortuous geometry, and observed a range of selectivities dependent on the
  anion coordinated to the LLC monomer.\cite{dischinger_effect_2017} Intelligent 
  design of LLC monomers can help us tailor membranes for solute-specific
  separations.

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.\cite{zhou_supported_2005}
  While size-exclusion is a useful separation, it cannot reliably purify a 
  solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  Unfortunately, the complexity of LLC Membranes has obscured the interpretation
  of experimental transport studies.\cite{dischinger_effect_2017}  % BJC: ref to Sarah?

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can directly observe small solute transport
  within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations.

  In our previous work, we used MD simulations to determine the most likely 
  structure of the hexagonal phase formed by the monomer Na-GA3C11, expanding 
  upon the most recent experimental characterization.\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting
  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
%  Many of the separations we are interested in involve polar organic 
%  compounds.

  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
  % them much thought. Just used their residue names
  \begin{table}
  \centering
  \begin{tcolorbox}[%
  	colframe=blue,
  	title=\centering \textbf{Solute Names and Their Abbreviations},
  	width=0.7\textwidth,
  	box align=center,
  	halign=center,
  	valign=center,
  	fontupper=\linespread{1}\selectfont]

  \begin{multicols}{2}

  \textbf{Name} \\
  Acetic Acid \\
  Acetamide \\
  Acetone \\
  Butanol \\
  Dimethyl Formamide \\
  2,3-Dimercapto-1-propanol \\
  Dimethyl Sulfoxide \\
  Ethyl Acetate \\ 
  Ethanol \\
  Ethylene Glycol \\
  Glycerol \\
  Methanol \\ 
  Propylene Carbonate \\
  Propylene Glycol \\
  Propanol \\
  Ribose \\
  Mercaptoethanol \\
  Tetrose \\
  Tetrahydrofuran \\
  Urea \\
  \columnbreak

  \textbf{Abbrevation} \\
  ACH \\  
  ACN \\
  ATO \\
  BUT \\
  DMF \\
  DMP \\
  DMSO \\
  EAC \\ 
  ETH \\
  GCL \\
  GLY \\
  MET \\
  PCB \\ 
  PG \\
  PR \\
  RIB \\ 
  SOH \\ 
  TET \\
  THF \\ 
  URE \\

  \end{multicols}

  \end{tcolorbox}
  \caption{}\label{table:abbreviations}
  \end{table}

  First, we will comment on the membrane's structure. Previously, we have
  studied dry membrane systems and some systems with low water content. 
  We will observe how the radial density of monomer components and water 
  change based on membrane water content.

  % BJC: I don't really explicity comment on the partitioning of solutes
  % out of the pore. Maybe I can add some sort of chart. Need to think more.
  Then we will present our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  it is straightforward to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We will study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.

  Finally, and for the bulk of this work, we will present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way. We want to understand
  the differences in solute motion, specifically its mean squared displacement 
  (MSD), based on a solute's size, shape and chemical functionality. We will 
  study the interactions between solutes, the membrane, and water in order to
  determine which mechanism or mechanisms dominate.

  There are also a couple of points that this study is not intended to address. 
  First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will be the same 
  regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. This information will not greatly enhance our
  understanding of mechanistic details in various membrane regions. Both of the
  above points will add unnecessary levels of complexity which can be left for
  a future study. This work is a simple starting point meant for observing
  the types of interactions which occur between isolated solutes and the
  membrane.

  \section{Methods}

  Python scripts used to set up systems and conduct post-simulation trajectory 
  analysis are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. 
  %BJC: also link to readthedocs? I have the link in the repo
  The appropriate scripts to use for the subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information.

  We ran all molecular dynamics simulations and energy minimizations using GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

  \subsection{System Setup}\label{method:system_setup}

  Stable H\textsubscript{II} phases, assembled with Na-GA3C11, can be formed
  using a broad range of water concentrations. In the literature, the system 
  studied in this work is typically synthesized with close to 10 wt \% water.
  \cite{smith_ordered_1997, zhou_new_2007} However, Resel et al. noted that the
  system is likely fully hydrated with less than 7 wt \% water.\cite{resel_h2-phase_2000}
  Excess water fills space between hexagonal mesophases. We decided to test 
  systems with two different water contents: 5 and 10 wt \%.

  We observed that water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95 \% of their time outside of the distal tail region.

  We equilibrated an initial solvated configuration before adding solutes. First, we 
  equilibrated the initial configuration using the `wet' equilibration procedure 
  described in our previous work. Then we cross-linked the equilibrated solvated 
  configuration using the cross-linking procedure also described in our previous 
  work.~\cite{coscia_understanding_2019}

  To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
  center of each pore of the equilibrated cross-linked configuration. Our choice of 6
  solutes per pore provided a balance of a useful amount of data for generating 
  statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate for 5 ns using berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations.

  \subsection{Solute Parameterization}\label{method:parameterization}

  We parameterized the interaction potential for the monomer and solutes using 
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
  We use GAFF since it has been parameterized for use with organic molecules. We
  assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
  with QUACPAC from Openeye Scientific Software.

  \subsection{Mean Squared Displacement}\label{method:MSD}

  We measured the time-averaged $z$-direction mean squared displacement (MSD) of the
  centers of mass (COM) of each solute over the course of 1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  Generally, the MSD grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

  % BJC: haven't talked about hopping mechanism at this point, but need to justify why
  % I used total MSD rather than fitting some function to it
  We fixed the length of each simulated trajectory so that we could compare the total
  MSD between different solutes without the influence of the ageing phenomenon.
  In systems such as ours where solutes show hopping behavior between long periods 
  of immobility, ageing is defined by the tendency of the average slope of an MSD 
  curve to decrease as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
  Since the maximum measured dwell time can be no longer than the total length of a simulated
  trajectory, longer dwell times are incorporated into the calculation as measurement
  time or trajectory length is increased, lowering the average MSD. Because the solute 
  MSDs are non-linear and because of the ageing phenomenon, we did not attempt to calculate
  a diffusion constant as one might for a Brownian particle with a linear MSD. Instead,
  the reported MSD values represent the average MSD for a given	solute after a 400
  ns time lag. Our results are shown to be insensitive to our choice of time lag in 
  Section~\ref{S-section:lag_sensitivity} of the Supporting Information.

  The $z$-direction MSD of water in the 10 wt \% system is linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured the diffusion coefficient in one 
  dimension.

  \subsection{Molecular Size Determination}\label{method:molecular_size}

  In order to determine an effective radius for each solute, we divided in 
  half the maximum pairwise distance between atoms of each solute over the course of
  a 2.5 ns simulation of solutes dissolved in a cubic box of water. Each box 
  consisted of about 2100 water molecules and 6 solutes. Although there exist
  more involved methods for determining the hydrodynamic radius~\cite{schultz_determination_1961},
  we chose to use a simpler and more intuitive metric since we are only interested
  in observing trends in the solute mean squared displacement as a function
  of solute size.

  \subsection{The Stokes-Einstein Relationship}\label{method:stokes}

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function that is inversely related to the
  particle's radius:
  \begin{equation}
  D = \dfrac{k_bT}{6\pi\eta fr}
  \label{eqn:stokes-einstein}
  \end{equation}
  where $k_b$ and $T$ are the Boltzmann	constant and the system temperature
  respectively and $\eta$ is the system's viscosity. Here we have also 
  included the microfriction correction factor, $f$, introduced by 
  Gierer and Wirtz~\cite{gierer_molekulare_1953,chen_diffusion_1984} for when
  solute size becomes on the order of solvent size since the solute can no 
  longer be treated as a non-interacting hard sphere. $f$ is defined in terms
  of the ratio of $r_1$ and $r_2$, the radii of the solute and solvent molecules
  respectively:
  \begin{equation}
  f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}
  %f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}
  \label{eqn:correction_factor}
  \end{equation}
  For consistency with the presentation of our results, rather than calculate trends
  in $D$, we will apply Equation~\ref{eqn:stokes-einstein} in order to analyze 
  trends in solute MSDs, which is only valid because all trajectories are of the 
  same length.
%  However, this assumes linear behavior
%  of the MSD, which we will show is not that case. Our main usage of the 
%  Stokes-Einstein relationship is to show that solutes in our system do not 
%  behave as it predicts.
  % Possible comps question: Stokes law restricted to Re < 0.1, but we have no flow so Re ~ 0.

  Since we will be using this equation for primarily qualitative observations, 
  we made a number of simplifying assumptions so that it could easily be used for 
  comparison between systems. First, we assume that all systems' viscosities
  are equal since we only make minor changes to the membrane's composition and
  accurately assessing the viscosity in a complex and inhomogeneous system such 
  as ours is a challenge by itself. Second, we assume all particles are approximately
  spherical, neglecting the effect of solute shape on mobility. Chan et al. 
  showed that the difference in diffusion constants of differently shaped 
  particles, with constant molecular volume, did not differ by more than 25 \%
  with most deviating by less than 10 \%.~\cite{chan_effects_2015}. 
  Third, we assume that the ratio of solute and solvent radii as calculated using the
  methodology of Section~\ref{method:molecular_size}, is equivalent to the the 
  ratio of hydrodynamic radii. For similarly shaped molecules, it has been shown that
  one can relate the hydrodynamic radius and radius of gyration (R\textsubscript{g})
  using a constant scaling factor. \cite{lee_molecular_2008,he_novel_2003,li_critical_2009}.
  % BJC: could just calculate Rg instead of end-to-end
  Assuming that our end-to-end distance reasonably approximates R\textsubscript{g} 
  for our small, relatively inflexible molecules, we believe this assumption is 
  justified for qualitative demonstrations relevant to this study.

  In order to make qualitative comparisons, we fit Equation~\ref{eqn:stokes-einstein}
  so that it passed through the highest solute MSD. We assumed that the solute
  with the highest MSD behaved the most ``Stokes-like" and therefore could set a
  rough boundary between subdiffusive, Brownian and superdiffusive MSDs. As a lower
  bound to our appoximation, we also plotted the uncorrected version of 
  Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the same 
  value as the corrected curve for large radii. 
  % BJC: Set really high intersection value. Converges quickly (i.e. critical radius
  % (the radius where curves intersect) of 2.5 nm looks almost the same as critical
  % radius of 100 nm. I don't think this necessarily needs to be proved anywhere

%  at the critical particle radius 
%  where the uncorrected Stokes-Einstein begins to break down. An exact critical
%  radius is not well-defined, but based on the observations of others, we will
%  approximate that radius as 2.5 nm\cite{li_critical_2009,polson_some_1950}. The 
%  sensitivity of the uncorrected curve to this intersection radius is shown to 
%  be small and is graphically illustrated in Section-TBD of the Supporting Information.

%  It is well-known that equation~\ref{eqn:stokes-einstein} breaks down Gierer and Wirtz introduced a microfriction
%  correction factor in order to address this issue. 
%  They proposed that 
%  \begin{equation}
%  D = \dfrac{k_bT}{6\pi\eta fr}
%  \end{equation}
%  where

  \subsection{Hop Detection}\label{method:hop_detection}

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement the $z$-direction.
  % BJC: could add more detail about which algorithm and cost function
  % penalty I used. Seems unnecessary since it is all in my code.

  \subsection{Identification of Hydrogen Bonds}\label{method:hbonds}

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  package which allows us to directly check the validity of identified hydrogen bonds.
  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
  show that our conclusions are insensitive to this definition within a 
  reasonable range.

  \subsection{Coordination Number}\label{method:coordination}

  We quantified the coordination of solute constituent atoms with sodium ions.
  For each frame, we counted the number of coordinated molecules to a
  given solute atom based on a distance cut-off. Using four different methods,
  Rowley and Roux observed peaks in the radial distribution function for sodium
  coordinated with water at an O--Na distance of between 2.3 and 2.5 \AA.
  \cite{rowley_solvation_2012} We used 2.5 \AA~as the distance cut-off. We 
  found that this approach is more useful than calculating the 3D spherical
  radial distribution function because it gives detailed frame-by-frame 
  information rather than an average.

  Using our procedure we found that sodium ions in a solution of tip3p water
  coordinate with an average of 3.6 water molecules. We created a 4 x 4 x 4
  nm cubic box of water with the GROMACS tool, \texttt{gmx solvate}. We used
  \texttt{gmx genion} to replace water molecules with sodium and chloride 
  ions in order to create a 0.1 M NaCl solution. We let the system simulate
  for 5 ns and reported the average number of coordinated water molecules 
  per frame after discarding the first nanosecond of simulation.

  \subsection{Association Lifetimes}\label{method:lifetimes}

  We quantified the length that two species stay associated via hydrogen
  bonding or coordination. For each unique pair, we measured the number of 
  consecutive frames in which they stayed associated. We considered pairs
  that disassociated for a single time step and reformed on the next time
  step as a single continuous association event. We compiled the length 
  of these events into a distribution of association lifetimes.
  %BJC: could justify why I didn't use autocorrelation functions

  We found that the distributions best fit a power law / exponential
  distribution.
  % BJC: need to do this. 
  % BJC: reporting median doesn't work great since it is usually equal
  % to the lowest possible value since time step is large.
  % Would probably be better to report fit parameters (alpha for power law)
  % Could use those values in analytical equations for median

  \subsection{Radial Distribution Functions}\label{method:rdfs}

  We measured the average radial distance of each solute of interest 
  from the pore centers. We binned the radial distances and then 
  normalized by the volume of the annulus defined by the bin edges.
  Although the pores are often described as straight, they have a
  small degree of tortuosity which disrupts the RDF calcuation. We 
  tried to mitigate the effects of tortuosity by calculating the RDF
  with respect to splines that run through the pore centers. See
  Section~\ref{S-section:splines} of the Supporting Information for 
  a graphical illustration. Each spline consists of 10 points, equally
  spaced in the $z$-direction, whose ($x$, $y$) coordinates are defined
  based on the center of mass of all head groups closest, in $z$, to the
  given point. When calculating RDFs, the radial distance from the pore 
  center is based on the distance between the solute center-of-mass and
  the linearly interpolated ($x$, $y$) coordinates of the pore center 
  calculated based on the closest two spline points. Using the splines, 
  % BJC: below to supporting?
  we calculated the tortuosity of the pores by calculating the ratio 
  $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is the 
  length of the unit cell in the $z$-direction. The average tortuosity
  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt \%
  water systems respectively.

  In all RDF plots, we include the average RDF of the head groups as
  a reference. The head group RDF shown is the average of the head 
  group RDFs for each solute system in the plot. We generated 
  95 \% confidence intervals by bootstrapping the RDF of each individual
  head group. For each head group, we obtained an RDF averaged over the
  entire simulation trjaectory. We randomly chose head group RDFs with replacement
  and averaged them for each bootsrap trial. This approach assumes that
  head group positions are uncorrelated.

  \section{Results and Discussion}

  \subsection{Structure of Membrane Constituents}\label{section:membrane_components}

  Before beginning the analysis of transport behavior, it is important to
  elucidate the topology of the membrane pores in solvated systems.

  In contrast to our previous work with a dry version of this 
  membrane, the pore region of the 5 and 10 wt \% water 
  systems are primarily filled with water and sodium ions. We define the
  pore region based on the average COM position of the monomer head groups' 
  % BJC: not sure the best place in paper to define pore region. Maybe a system definitions section in Methods.
  % BJC: need to decide on exact definition. Should probably be the same as the 'Head Groups' line
  carboxylate oxygen atoms. Figure~\ref{fig:component_densities} plots the RDF of each membrane
  constituent in the dry system as well as the 5 and 10 wt \% water systems. 
  In dry systems, the pore center is densely filled with sodium ions and head
  groups. The peak head group density occurs within 0.25 nm of the pore center.
  In hydrated systems, water occupies, and is densest, at the center of each 
  pore. The density of sodium ions is somewhat uniform in the pore center of
  the 5 wt \% water system while it shows a maximum closer to the head groups
  in the 10 wt \% water system. The peak density of sodium ions is not at the
  pore center in the 10 wt \% water system likely because they are still
  loosely associated with the monomer's carboxylate head groups.

  Pores in the 10 wt\% water system are wider and less crowded by monomers than
  those in the 5 wt\% water system. The peak head group density of 10 wt\% water
  systems is about 0.2 nm further from the pore center than the 5 wt\% water system. 
  Based on these observations, we expect solute transport to be fastest in the 10 wt
  \% water system.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_dry.pdf}
  %BJC: simulation is extended to smooth out these curves
  \caption{Dry System}\label{fig:component_density_dry}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a 
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to 
  the color-coded monomer pictured in the upper right corner of the figure. 
  All RDFs represent the number of atoms located at a given distance from the
  pore center normalized by the volume of the annular bin to which they belong.
  (a) In the dry system, the density of head groups and sodium ions are highest
  within 0.25 nm of the pore center. (b) In the 5 wt \% system, monomer head 
  groups retreat about 0.2 nm radially in order to make room for water molecules.
  (c) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
  for more water.}\label{fig:component_densities}
  \end{figure}

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28 \% and 31 \% of the total water is present in the tail
  regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information for more details. This 
  result is due to a combination of the lower density of the tail region
  as well as oxygen atoms at the ends of each monomer tail which can further 
  stabilize water molecules. See Figure~\ref{S-fig:total_density} of the 
  Supporting Information for a graphical illustration of this point.

  \subsection{Mechanisms Governing Small Solute Transport}\label{section:mechanism_overview}

  We observed transport of sodium, water and 20 other small polar solutes
  inside the membrane nanopores. First, we will comment on transport of the
  membrane constituents, water and sodium, in a system absent of any additional
  solutes. Then we will present the general trends that we observe among the
  set of solutes studied.

  \subsubsection{Water and Sodium Ions}\label{section:transport_water_sodium}

  Water and sodium's mobilities increase in larger and less crowded pores. 
  In the 10 wt\% water system, the MSD of water is about 51 times higher and
  the MSD of sodium is about 49 times higher compared to the 5 wt \% water system. 
  In the 10 wt \% water system, water moves about 51 times faster than sodium 
  and in the 5 wt \% system, water moves about 49 times faster than sodium. Assuming
  long timescale Brownian behavior of water in the 10 wt \% system, we measured its
  diffusivity to be 7.45e-07 $cm^2 / s$ which is only 1.4 \% that of bulk tip3p 
  water.~\cite{mahoney_diffusion_2000} %BJC: 7.45e-07 versus 5.19e-05 cm^2/s

  % Plots generated with msd_curves.py in figures folder
  % BJC: I show up to 400 ns time lag. Any reason to show full 1000 ns?
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{water_msd_comparison.pdf}
  \caption{Water}\label{fig:water_msd_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{na_msd_comparison.pdf}
  \caption{Sodium Ions}\label{fig:na_msd_comparison}
  \end{subfigure}
  \caption{(a) The MSD of water in the 10 wt \% water system is about 51 times
  higher than water in the 5 wt \% water system. (b) The MSD of sodium in the
  10 wt \% water system is about 49 times higher than sodium in the 5 wt \% 
  water system.}\label{fig:msd_comparison}
  \end{figure}

  Sodium coordinates with far less water molecules than it does in bulk solution.
  Compared to 3.4 coordinated water molecules in bulk solution (see 
  Section~\ref{method:coordination}), sodium ions in our system, on average,
  coordinate with about 1.7 water molecules in the 10 wt \% system and 1.2 water
  molecules in the 5 wt\% system. However, the sodium ions are not undercoordinated
  since they frequently pair with negatively charged carboxylate head groups.
  On average, sodium ions coordinate with 1 carboxylate group in the 10 wt \% water
  system and 0.8 carboxylate groups in the 5 wt \% water system.
  % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
  % since the averages were divided by 800 instead of 400

  \subsubsection{Transport of Small Polar Solutes}\label{section:general_transport_solutes}

  We observe trends in transport properties that are dependent on the chemical 
  environment within the nanopores rather than just solute size. Polar solutes
  are slowed by interactions between monomer functional groups and ions. Solutes
  with hydrophobic character partition out of the pore and are slowed by densely
  packed organic monomer components. A thorough understanding of these interactions
  will help us to create monomer design principles. We will begin our analysis by
  considering the collective trends observed across all systems and then focus on
  subsets of similar molecules.
%  where some exceptions occur.

%  We have gained a clearer picture of the general transport properties exhibited by
%  this system through the collective study of all solutes. We will first address the
%  questions posed in the introduction in a general sense before addressing them with
%  respect to specific molecules, where exceptions occur.
%  \bigskip

  Like water and sodium above, the MSDs of the solutes studied in this work are 
  significantly larger in the 10 wt \% system than those in the 5 wt \% water 
  system (Figure~\ref{fig:msds}). The fastest moving solute in both cases, 
  methanol, has an MSD about 175 times larger in the 10 wt \% versus the 5 wt 
  \% water system. Clearly the equilibrium water content of a given LLC system will 
  determine its viability for real separations.

  The MSDs are not solely a function of solute size. We plotted each solute's radius
  against their MSD in Figures~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
  Of all the solutes, we believe methanol is subject to the least hindrance by
  the membrane due its small size. Therefore we fit Equation~\ref{eqn:stokes-einstein}
  so that it intersected methanol's MSD. The uncorrected version of 
  Equation~\ref{eqn:stokes-einstein} is plotted and converges to the same value as the
  corrected form for large radii (see Section~\ref{method:stokes}). Although both curves are 
  approximations, they illustrate that the majority of solutes in our study show
  lower than expected MSDs. In most cases, the predicted MSDs even fall below the 
  conservative uncorrected Stokes-Einstein estimate. It is clear that more complex
  mechanisms determine the MSDs of these solutes.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

  On the timescales simulated in our study, solutes exhibit subdiffusive
  behavior. Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus
  time of 3 representative ethanol centers of mass in the 10 wt \% water system.
  There are clear periods of entrapment separated by relatively large hops.
  The MSD calculated based on all ethanol molecules is plotted in 
  Figure~\ref{fig:example_msd} and its shape is sublinear. The long periods
  of entrapment lead, in part, to this sublinear, and thus subdiffusive, behavior.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and the hops occur when solutes are close to the pore center. (b) The
  time-averaged MSD of ethanol is sub-linear which suggests transport is governed 
  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
  \end{figure}

  The complex and non-homogeneous structure of the membrane leads to radially
  dependent transport mechanisms. In general, we observed that hops 
  made in the pore region are about 45 \% larger than those made outside
  the pore region (See Figure~\ref{fig:hop_lengths}). There is a high 
  resistance to movement in the alkane-dense head group and tail regions
  while, in the pore region, solutes can move relatively freely since it 
  is primarily composed of water molecules. However, time spent in the 
  pore region does not necessarily lead to more frequent hopping. The 
  largest solutes in this study spend the most time in the pore region
  (see Figure~\ref{fig:frac_time}), but many hop with a below-average
  frequency (see Figure~\ref{fig:hopfreq}). Therefore, trapping mechanisms
  controlled by membrane properties other than density must be prevalent.

%  Solutes partition out of the pore into the head group region and beyond
%  which may lead to a radially dependent transport mechanism. It is clear 
%  from Figure~\ref{fig:example_ztraces} that the longest periods of 
%  entrapment usually occur when solutes are far from the pore center.

  % When hops occur, and where there is the most $z$-positional
  % noise, solutes are generally close to the pore center

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{hop_length.pdf}
  \caption{}\label{fig:hop_lengths}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{frac_time_spent.pdf}
  \caption{}\label{fig:frac_time}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hopfreq_total.pdf}
  \caption{}\label{fig:hopfreq}
  \end{subfigure}
  \caption{(a) Hops made in the pore region of the 10 wt \% water system 
  are, on average, 45 \% larger than those made outside the pore region. 
  The trend in hop lengths is similar to the trend in MSDs shown in 
  Figure~\ref{fig:all_msds_10wt} implying that solutes which make consistently 
  larger hops have higher MSDs. The fraction of time spent by a solute in the 
  pore region (b) does not necessarily lead to more frequent hopping (c). For
  example, ribose spends the largest fraction of time in the pore region, yet
  performs the the second lowest number of hops.}\label{fig:hops}
  \end{figure}

  In addition to solute trapping in dense monomer regions, 
  we observe a second trapping mechanism caused by preferential hydrogen 
  bonding between hydrogen bond donor solutes and monomer head groups. To 
  continue with our ethanol example, we observe that 64 \% of ethanol 
  molecules donate hydrogen bonds  % 15.7/24 donated, 0.6/24 accept -- BJC: double check these numbers
  and 3 \% of ethanol molecules accept hydrogen bonds each frame. On average, 40 \%
  of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
  head groups, 25 \% go to the ether linkages between the tails and the 
  head groups and the remaining 35 \% to water. There are about 46 \% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molcules in pores 
  carboxylate oxygen atoms in the pore than there are water molecules yet more
  hydrogen bonds are donated to them. The stability of hydrogen bonds with 
  carboxylate oxygen atoms is high because they have a negative charge
  with no neutralizing positive charges nearby. Additionally, on average, 
  each sodium ion is coordinated to 1.7 water molecules meaning an appreciable
  fraction of the water molecules occupying the pore region are usually 
  coordinated to a sodium ion which decreases their availability to accept 
  hydrogen bonds from solutes.
  % MRS1: this should lead to reduced ability to solvate positive things, but 
  % shouldn't reduce H-bonding that much?
  % BJC1: I think that it takes away acceptor oxygen atoms since they are occupied
  % by sodium. The hydrogen atoms of water could still hbond but I'm just talking
  % about ethanol donating to water's oxygen, for which opportunities should be suppressed.

  The lifetime of hydrogen bonds between solutes and monomer head groups tends to 
  be longer for solutes that hydrogen bond more frequently. In Figure~\ref{fig:hbonds}
  we see nearly the same ordering of the percentage of solutes hydrogen bonded to
  monomer head groups and the mean hydrogen bond lifetime. Solutes with multiple
  hydroxyl groups donate hydrogen bonds most frequently and tend to stay hydrogen
  bonded longer. Hydrogen bonds donated by nitrogen are far less common and tend 
  to be short-lived as supported by acetamide and urea.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nhbonds_all.pdf}  % unique_hbonds.py
  \caption{}\label{fig:nhbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hbond_lifetime.pdf}  % hbond_dwells.py
  \caption{}\label{fig:hbond_dwells}
  \end{subfigure}
  \caption{(a) Solutes capable of donating hydrogen bonds to monomer head groups
  do so to varying degrees. The reported percentages represent unique solute-monomer
  hydrogen bonds. Individual solutes that hydrogen bond with multiple head groups
  simultaneously are only counted once. (b) The lifetime of individual hydrogen
  bonds appears correlated to the percentage of solutes involved in hydrogen bond
  interactions. Hydrogen bond lifetimes tend to be longer for solutes that 
  hydrogen bond frequently. Note that solutes incapable of donating hydrogen
  bonds are omitted from this figure.}\label{fig:hbonds}
  \end{figure}

  Finally, we observe slowing or immobilization of solutes that associate with
  sodium counterions. Much like water, the polarity of the solutes creates 
  regions of high electron density, modeled using partial negative charges, 
  which are stabilized through electrostatic interactions with sodium ions. 
  In Figure~\ref{fig:na_coordination}, we've plotted the percentage
  of sodium ions coordinated to the oxygen atoms of each solute as well as the
  average length of time that pairs stay coordinated. The degree and length of 
  coordination between solutes and sodium in the 5 wt \% water system is higher
  in all cases than that in the 10 wt \% water systems. The crowded pores of 
  the 5 wt \% water system forces sodium ions in close proximity to solutes. 
  The 5 highest coordinated solutes, which also have the longest coordinated dwell times,
  all contain carbonyl groups (except for dimethyl sulfoxide which has an 
  analogous sulfinyl group) which leaves a highly electron-dense oxygen atom 
  exposed and ready to interact with sodium. 
  %BJC: need to verify following  
  The dwell times are power law 
  distributed, which means that while many of these interactions are fleeting,
  there is still a chance for very long periods of association to occur. For 
  example, the longest period of coordination between acetone and sodium was
  110 ns.
%  There are many cases, particularly when an electronegative atom is left unprotected,
%  in which polar groups bind to sodium ions for at least a short period of time.

  % need to think a little more about this. Numbers get skewed by different numbers
  % of oxygen atoms per solute. For example, the carbonyl group of acetic acid
  % associates with sodium a lot, but the OH doesn't really. (28 % C=O versus 3 % COH)
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_solutes_NA_coordination.pdf}
  \caption{}\label{fig:all_solutes_NA_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_NA_dwells.pdf}
  \caption{}\label{fig:all_NA_dwells}
  \end{subfigure}
  \caption{(a) Solutes, especially those with carbonyl groups, spend a 
  significant fraction of time coordinated to sodium ions. (b) The length
  of time a solute-sodium pairs spends associated tends to be higher for
  pairs that associate more frequently.}\label{fig:na_coordination}
  \end{figure}

  Coordination of ions with oxygen has been observed in a variety of systems. 
  Carvajal et al. noted that Na\textsuperscript{+} coordinated with four 
  tetrahydrofuran molecules when they dissolved a sodium salt in the solvent.~\cite{carvajal_studies_1965}
  Wu et al. observed coordination of Na\textsuperscript{+} with the carbonyl
  group of a molecule used to design an organic electrode.~\cite{wu_unraveling_2015} 
  Finally, Shinoda et al. observed K\textsuperscript{+} ions coordinated with
  the carbonyl and hydroxyl groups of carboxy-terminal groups in crystallized
  ATPase.\cite{shinoda_crystal_2009}

  Overall, the transport behavior exhibited by solutes in the 5 wt \% water
  systems is similar to that shown by those in the 10 wt \% system however
  the timescales are much longer. We observe subdiffusive behavior with 
  intermittent hopping between periods of entrapment and evidence
  of the same three trapping mechanisms. The frequency and 
  length of hops are both diminished in the 5 wt \% system. Since there are
  only 24 solute molecules in each system, in order to obtain better 
  time-averaged descriptions of solute transport mechanisms, we will focus
  the remainder of our analysis on transport in the 10 wt \% water systems.

  We will revisit our observations in the the context of specific groups of 
  molecules in the discussion that follows.
  % We will make reference to the figures in this section

  \subsection{Transport of Simple Alcohols}

  The MSDs of methanol, ethanol, propanol and butanol descend in order of 
  their size. Using methanol as a reference, the larger alcohols move slower
  than expected according to both the pure Stokes-Einstein relationship 
  and the corrected relationship (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}).

  Methanol has the highest MSD of all solutes because it makes the most frequent
  and longest hops (see Figure~\ref{fig:hops}). Somewhat counterintuitively, 
  methanol, along with the other simple alcohols, spends a smaller fraction of its
  time in the pore region than most other solutes. However, even outside the pore
  region, hops made by methanol are larger than those by any other solute. The
  small size of methanol allows it to move relatively unhindered.

  The RDFs of longer chain alcohols show a sharp peak near the head groups 
  (see Figure~\ref{fig:simple_alcohol_rdf}). On average, the density of methanol
  in the pore center is only slightly less than its density near the head 
  groups while all other alcohol molecules are most concentrated near the head
  groups.
  % BJC: could say something like the following
  % The hop lengths and frequencies are not exceedingly small for any of the
  % simple alcohols, but their high density near the head groups suggests that
  % the hops may be anti-correlated, yielding low MSDs especially as the solutes
  % get larger.

%  Methanol moves fast because it is the smallest solute studied in this work and
%  it has a high radial density near the pore center where the largest hops occur.  % actually spends a small amount of time there relative to other solutes.
%  The radial density as a function of distance from the pore center for each
%  alcohol is plotted in Figure~\ref{fig:simple_alcohol_rdf}. On average, the 
%  density of methanol in the pore center is only slightly less than the density
%  near the head groups. All other alcohol molecules are most concentrated near 
%  the head groups.

  All simple alcohols participate in a similar number of hydrogen bonding 
  interactions with the monomer head groups, but with varying preference towards
  hydrogen bonds with the monomer carboxylate oxygen atoms over the ether oxygen
  atoms that connect the tails to the head groups (see Figure~\ref{fig:simple_alcohol_hbonds}).
  If all 5 hydrogen bonding acceptor sites on the monomer head groups were equal,
  we would expect the ratio of the number of hydrogen bonds between solutes and
  the two carboxylate oxygen atoms to the number of hydrogen bonds between solutes
  and the three ether groups to be 2/3. There is a clear preference towards 
  hydrogen bonding with the carboxylate oxygen atoms for all simple alcohols. 
  This is largely due to the large net charge of the carboxylate groups as well
  as the more highly crowded environment surrounding the ether oxygen atoms. 
  Butanol shows the largest preference towards hydrogen bonds with carboxylate
  head groups. The radial distribution function of atoms located at opposite ends
  of butanol shows that, on average, oxygen atoms are situated closer to the pore
  centers than the most distal carbon atoms. This suggests that alcohols tend to 
  orient themselves like the liquid crystal monomers, with hydrophilic components
  directed towards the pore centers.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols_10wt.pdf}
  \caption{}\label{fig:msd_radius_simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
  \caption{}\label{fig:simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
  \caption{}\label{fig:simple_alcohol_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{butanol_CO.pdf}\lapbox[\width]{-2.85cm}{\raisebox{3cm}{\includegraphics[height=1.4cm]{butanol_labeled.pdf}}}
  \caption{}\label{fig:butanol_CO}
  \end{subfigure}
  \caption{(a) The MSD of the simple alcohols decrease as a function of the
  solute size, however the MSDs of ethanol, propanol and butanol are considerably
  lower than expected based on the Stokes-Einstein equation. (b) The radial 
  distribution functions of each simple alcohol shows a maximum close to the
  highest density of monomer head groups (normalized based on propanol's maximum
  density for easier visual comparison). Methanol spends the largest proportion 
  of time, relative to the other alcohols, near the pore center, which may help
  explain its fast dynamics. (c) Despite relatively little difference in the 
  total number of solutes actively participating in a hydrogen bond each frame,
  a given alcohol's preference towards hydrogen bonds with the carboxylate groups
  of ether linkages increases with molecule size. (d) The average location of 
  butanol's oxygen atom is closer to the pore center than its most distal carbon
  atom, suggesting that the molecule is oriented with hydrophobic tails pointing
  away from the pore center.}\label{fig:simple_alcohols}
  \end{figure}

  \subsection{Transport of Diols, Triols and Sugars}\label{section:polyols}

  The order of the MSDs of solutes in this grouping are roughly consistent with 
  their size, however propylene glycol moves exceptionally slow (see 
  Figure~\ref{fig:polyols_msd}). Ethylene glycol has the highest MSD followed
  by tetrose and glycerol, whose MSDs are similar, propylene glycol, the second
  smallest	solute of this set, and finally ribose.

  Transport is both facilitated and hindered by additional solute hydroxyl groups
  due to their influence on radial density and hydrogen bond frequency. Extra 
  hydroxyl groups cause solutes to favor the water-rich pore region where there 
  is the least hindrance to movement (See Figure~\ref{fig:polyols_rdf}). Tetrose,
  ribose and glycerol are densest close to the pore center. They spend a greater
  fraction of their time in the pore region than any other solute (see 
  Figure~\ref{fig:frac_time}) This is likely a consequence of both their 
  hydrophilicity and large size which prevents them from partitioning into the 
  head group region. However, these extra hydroxyl groups facilitate a larger 
  number of hydrogen bond interactions that work to hold solutes in place (see 
  Figure~\ref{fig:multi_hbonds}). It has been observed that hydrogen bonding 
  in a system will generally reduce diffusivity.\cite{srinivas_computer_1999}

  The number of hydrogen bonding interactions between solutes and head groups
  increases with the number of solute hydroxyl groups. These solutes frequently
  undergo simultaneous hydrogen bond interactions as shown in 
  Figure~\ref{fig:multi_hbonds}. For example, both hydroxyl groups of ethylene
  glycol can undergo hydrogen bonds with different hydrogen bond acceptors at 
  the same time. In some cases, all 4 hydroxyl groups of ribose hydrogen bond
  to monomer head groups simultaneously. As a consequence, hydrogen bond 
  lifetimes in these cases tend to be longer (see Figure~\ref{fig:hbond_dwells})
  since the solute positions are stabilized by multiple interactions. When one
  hydrogen bond is broken, the remaining unbroken hydrogen bonds keep the 
  molecule in place and allow the previously broken bond to reform.
%  Hydrogen bonds act as a kind of 
%  molecular glue which holds solutes in place, especially when there are many.
  Proximity to the pore center partially compensates for this effect in
  the cases of glycerol and tetrose, causing them to have relatively high MSDs
  for their size.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{msd_radius_diols_10wt.pdf}
  \caption{}\label{fig:polyols_msd}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{polyols_rdf.pdf}
  \caption{}\label{fig:polyols_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \vspace{-0.275cm}
  \includegraphics[width=\linewidth]{multi_hbonds.pdf}
  \caption{}\label{fig:multi_hbonds}
  \end{subfigure}
  \caption{(a) The MSDs of the solutes in this set descend in order of their size, except
  for propylene glycol which moves exceptionally slow. The MSD of ethylene glycol 
  is in close agreement with the theoretical lines, implying that the solute 
  is subject to a similar amount of hindrance as methanol, the solute to which the
  theoretical lines were fit. (b) Glycerol, tetrose and ribose have high densities 
  close to the pore center because they have a high number of hydrophilic groups and
  are relatively large. Ethylene glycol and propylene glycol are densest close to the
  head group region. (c) The number of hydrogen bond interactions between solutes and
  monomers increases as solutes gain additional hydroxyl groups. The number of 
  hydrogen bonds made by a single solute in different locations simultaneously, n, 
  also increases with the number of hydroxyl groups. In the most extreme case, all 
  four hydroxyl groups of Ribose (n = 4) are involved in a hydrogen bond interaction
  at the same time.}\label{fig:multi_hbonds}
  \end{figure}

  Of the two diols, ethylene glycol moves significantly faster than propylene
  glycol due to propylene glycol's affinity for the monomer head groups.
  Combined with an increase in size, the addition of a single methyl group to
  ethylene glycol increases propylene glycol's hydrophobic character and causes
  it to favor positions near monomer head groups. Both diols have comparable 
  densities close to the pore center, however propylene glycol's density has a
  large peak near the monomer head groups relative to ethylene glycol. Propylene
  glycol can form more highly stabilized hydrogen bonds with carboxylate groups,
  explaining the slightly higher incidence of hydrogen bonds shown in 
  Figure~\ref{fig:multi_hbonds}. The average hydrogen bond lifetime of propylene
  glycol with monomers is 1.95 ns compared to 1.34 ns for ethylene glycol.  % BJC: 2.33 ns vs 1.62 ns for hbonds with carboxylate
  Somewhat counterintuitively, there is a relatively high density of ethylene
  glycol molecules beyond the head group region probably due to its relatively 
  small size. This likely contributes to the somewhat large error bars on its MSD
  in Figure~\ref{fig:msds}.

  \subsection{Transport of Ketones and Amides}

  The 4 ketone-like molecules tested show a surprising range of transport
  behaviors. Urea, acetic acid, acetamide and acetone are all characterized by
  a carbonyl group with two attached heavy atoms. All are similar in size and
  are planar molecules due to the sp2 hybridization of their carbonyl group. 
  The fastest solutes of this grouping, acetic acid and urea, move about 3
  times faster than the slowest, acetone.

  The amides, urea and acetamide, hydrogen bond with head groups relatively 
  infrequently, but regularly coordinate with sodium ions (see 
  Figure~\ref{fig:ketones}). In an average frame, over 50 \% of acetic acid molecules
  participate in hydrogen bonds with monomer head groups while less than 
  10 \% of urea and acetamide molecules hydrogen bond with head groups. 
  Urea and acetamide both have hydrogen bond donating nitrogen atoms, however
  nitrogen is a weaker hydrogen bond donor than oxygen due to its lower 
  electronegativity.\cite{biswal_hydrogen_2015} Given their lower propensity
  to hydrogen bond, one might expect amides to partition out of the pore 
  and/or to move through the pore quickly, perhaps faster than methanol. 
  However, both RDFs contain sharp peaks situated between the pore center
  and the head groups, but closer to the pore center than other solutes 
  that hydrogen bond with carboxylate groups. Solutes that
  hydrogen bond frequently tend to show peaks in their RDFs near 0.5-0.6 nm 
  from the pore center (see Figure~\ref{fig:simple_alcohol_rdf}, for example)
  and those that coordinate with sodium ions more frequently tend to show 
  peaks in their RDFs near 0.2-0.4 nm from the pore center. Both solutes spend
  about half of their time with their carbonyl oxygen atom coordinated to a
  sodium ion which restrains the solutes to within the pore region

  Among the solutes in this set, only the carbonyl oxygen atoms coordinate 
  with sodium ions. The nitrogen atoms do not coordinate at all despite a
  similar negative partial charge because the attached hydrogen atoms 
  shield this interaction by making the NH\textsubscript{2} group 
  approximately neutral.

  Acetone has the lowest MSD of this set because it either coordinates with
  sodium or stays trapped near and behind the head groups. Acetone spends the
  smallest fraction of time in the pore region out of all solutes in this study
  (see Figure~\ref{fig:frac_time}). On average, acetone coordinates with sodium
  with the same frequency as acetic acid which is manifested as a peak in its 
  RDF about 0.2 nm from the pore center. 
%  However, acetic acid spends 
%  significantly more time in the pore center and therefore encounters more sodium ions. 
  %When an acetone molecule coordinates with a sodium ion, its polarity is
  %largely neutralized and it retreats towards the head group region where it can easily
  %get trapped. 
  Acetic acid and the amides have other, unoccupied, hydrophilic groups while
  bound to sodium ions which increases their stability in the pore.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_ketones_10wt.pdf}
  \caption{}\label{fig:ketones_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{ketone_rdf.pdf}
  \caption{}\label{fig:ketones_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}
  \caption{}\label{fig:ketone_hbonds}
  \end{subfigure}
  \caption{(a) The MSD of the solutes decreases and the deviation from
  Stokes-Einstein predicted behavior increases as with molecular size increases.
  (b) The radial density near the pore center (r = 0) decreases with decreasing
  solute MSD. Peaks in the RDFs of urea, acetamide and acetone that appear 
  0.2 - 0.4 nm from the pore center are likely due to coordination with sodium
  ions. (c) The amides hydrogen bond with water far less than acetic acid, 
  however they tend to coordinate with sodium ions more frequently. Acetone
  coordinates with sodium with same frequency as acetic acid.}\label{fig:ketones}
  \end{figure}

  \subsection{Transport of Thiols}

  We also studied the transport properties of sulfur analogs of glycerol,
  ethylene glycol and acetone. We replaced all but one oxygen atom of 
  ethylene glycol and glycerol with sulfur atoms to create dimercaptoethanol
  and 2,3-dimercapto-1-propanol. We replaced the carbonyl carbon of acetone
  with sulfur in order to create DMSO. Sulfur-containing compounds form weaker
  hydrogen bonds than nitrogen and oxygen-containing compounds due to their
  low electronegativity.~\cite{biswal_hydrogen_2015} For this reason, thiols
  are less soluble in water than their hydroxyl group analogs.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  %BJC: should I plot ethylene glycol, glycerol and acetone MSDs here as well?
  \includegraphics[width=\textwidth]{msd_radius_sulfur_10wt.pdf}
  \caption{}\label{fig:SOH_GCL_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
  \caption{}\label{fig:SOH_GCL_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMS.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \caption{(a) The RDF of mercaptoethanol is similar to ethylene glycol except 
  for its higher density in the tail region and consequently lower density in the
  pore region. (b) 2,3-dimercapto-1-propanol is densest near the head groups, 
  unlike glycerol whose density is very high close to the pore center. 
  (c) Overall, dimethylsulfoxide has a higher density than acetone within the 
  pore region which may in part explain its marginally larger MSD.}\label{fig:sulfur_analog_rdfs}
  \end{figure}

  Mercaptoethanol has a similar average MSD and RDF to ethylene glycol.
  There is a much larger uncertainty associated with mercaptoethanol's
  MSD. The range of behaviors shown by mercaptoethanol help explain the
  large variance of its MSD. Some can be accounted for by the higher 
  density of mercaptoethanol molecules outside the pore region, where 
  transport is inherently slower. Mercaptoethanol spends 20 \% less 
  time in the pore region than ethylene glycol. Conversely, 
  mercaptoethanol hydrogen bonds with head groups about 40 \% less 
  frequently, which is less than expected if equal amounts of both 
  solutes occupied the pore region. Consequently, shorter hydrogen 
  bond lifetimes within the pore region may yield some high MSD 
  trajectories.

% (20.2 - 12.857) / 20.2 = .364
% (12.857 + 6.8215 + 0.803) / (20.2 + 11.969 + 1.935) = 0.6
%  There are nearly 40 \% more mercaptoethanol 
%  molecules than ethylene glycol molecules beyond 0.8 nm  % ratios.py in figures folder
%  from the pore center. 
%  The average length
%  of a hop performed by a mercaptoethanol molecule within 0.8 nm of the pore 
%  center is 1.43 nm compared to 1.20 for ethylene glycol. % hop_location.py. Even larger difference if cut-off lower

  2,3-dimercapto-1-propanol exhibits slower transport than glycerol 
  because more of it partitions into the tail region. 2,3-dimercapto-1-propanol
  spends 38\% less time in the pore region than glycerol.
%  The density of glycerol is always higher up to 0.7 nm from the pore center where the 
%  population of 2,3-dimercapto-1-propanol then becomes more dense into the tail region.
  Glycerol participates in about 2.5 times as many hydrogen
  bonds as 2,3-dimercapto-1-propanol. % which is consistent with the number of hydroxyl groups per solute. 
  % BJC: sums are (donate to monomer + recieve from water + donate to water).
  % BJC: (31.91 + 17.224 + 3.231) / (13.1 + 7.737 + 0.8965) ~= 2.45.
  % (2.788 + 2.0975 + 0)/ (13.1 + 7.737 + 0.8965) = 0.22
  Only 22 \% of the hydrogen bond interactions of 2,3-dimercapto-1-propanol
  involve sulfur. Because sulfur can only weakly hydrogen bond, 
  2,3-dimercapto-1-propanol is less soluble than glycerol in the water-filled
  pores and more readily partitions into the tail region.

  DMSO has a comparable if not larger MSD than acetone even though it
  is a slightly larger molecule. DMSO spends 17 \% more time in the pore
  than acetone. 
%  The density of DMSO is higher than acetone in the pore region, except for
%  the peak exhibited by acetone near 0.2 nm, which is due to sodium ion association.
  On average, 35 \% of DMSO molecules are coordinated to a sodium ion each
  frame compared with 26 \% of acetone molecules. The pyramidal structure 
  of DMSO may force it to spend more time closer to the pore center which
  increases its interaction with sodium ions. The tendency of DMSO to stay
  in the pore region counterbalances the sodium ion interactions to give it
  a higher MSD than acetone.

  \subsection{Hydrogen Bond Acceptors}  % Need a better heading since all molecules in this study are acceptors

  The slowest set of molecules we studied can accept hydrogen bonds, but
  cannot donate them. Among this set are the two slowest solutes in our study: 
  tetrahydrofuran and dimethyl formamide. The MSDs of ethyl acetate, propylene
  carbonate and acetone are only marginally larger.

  The solutes in this set have small hop lengths. 3 of the bottom 6 mean hop
  lengths are associated with ethyl acetate, propylene carbonate and
  dimethyl formamide (Figure~\ref{fig:hop_lengths}). Acetone and 
  tetrahydrofuran perform slightly larger hops but have the third and
  first lowest hop frequencies respectively (see Figure~\ref{fig:hopfreq}).

  The radial density of solutes near the pore center in this set is 
  surprisingly high as shown in Figure~\ref{fig:nondonors_rdf}. Propylene
  carbonate and ethyl acetate are among the largest solutes in this study. 
  Their size prevents them from easily entering the tail region and 
  consequently leads to faster transport properties.  % since they spend more time in the pore region. 
  However, this is not a hard rule. When a solute does overcome the 
  barrier of entry beyond the head group region, it can become trapped. All
  solutes in this set show at least a small peak $\geq$ 0.9 nm from the pore 
  center which is likely caused by solutes that get trapped in the tail region
  for significant periods of time.

%  The solutes in this set do not make frequent hops while in the pore region. 
%  % Time bound to sodium ion
%  % Number of hops in pore region
%  \begin{itemize}
%%	\item Observations of single THF trajectories have revealed that it becomes 
%%	nearly immobilized while associated with sodium ions 
%%	(See Figure~\ref{fig:thf_sodium_coordination}).
%	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
%	higher than THF near the head groups. The planar shape of DMF causes it to 
%	become stuck between head groups. Excursions into the pore region do not
%	necessarily result in large hops.
%  \end{itemize}

  Carbonyl groups continue to show high degrees of association with
  sodium ions. Between 25 and 30 \% of propylene carbonate, dimethyl 
  formamide and ethyl acetate molecules are coordinated with sodium ions
  for a given frame which is consistent with the coordination exhibited by acetone
  (see Figure~\ref{fig:nondonors_hbonds}). The carbonyl group of the amides 
  studied in the previous section associate with sodium nearly twice as 
  frequently as compounds that don't contain nitrogen 
  (see Figure~\ref{fig:ketone_hbonds}).
  Assocaition between sodium and solutes in this set are also among the longest,
  only beat by other solutes with carbonyl groups and ribose.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_nondonors_10wt.pdf}
  \caption{}\label{fig:nondonors_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{nondonors_rdf.pdf}
  \caption{}\label{fig:nondonors_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{nondonor_hbonds.pdf}
  \caption{}\label{fig:nondonors_hbonds}
  \end{subfigure}
  \caption{(a) The MSDs of solutes that can only receive hydrogen bonds are
  significantly lower than expected. (b) The solutes' radial density
  is surprisingly high in the pore region, but is balanced by an appreciable
  amount of solute trapped in the tails. (c) The low MSDs exhibited by each of these
  solutes is due to a combination of entrapment within the tail region and a high 
  degree of coordination with sodium ions.}\label{fig:nondonors}
  \end{figure}

  \section{Conclusion}

  We have examined the transport characteristics of a series of small polar
  molecules in our model of the H\textsubscript{II} phase formed by the liquid 
  crystal monomer Na-GA3C11.

  We learned that the MSD of solutes, water and counter ions are highly 
  dependent on LLC membrane water content. The MSD of these components is about
  2 orders of magnitude larger in the 10 wt \% system than in the 5 wt \% system.
  As more water is added to the system, the pores become less crowded with monomer
  components. The amount of water in the pores deserves special attention when 
  screening new monomers.

  We observed three mechanisms of solute entrapment.
  \begin{enumerate}
    \item A solute can become stuck among monomer tails. 
    \item A solute can donate hydrogen bonds to immobile monomers.
    \item A solute can associate with a bound counterion.
  \end{enumerate}

  Based on these trapping mechanisms, we can suggest modifications that
  can be made to monomers in order to mitigate or enhance their effect on
  solute MSDs. Since solutes move slowly while entangled among the monomer
  tails, one can try to design monomers that better control the partition
  of solutes between the pore and tail region. For example, removal of the 
  ether linkages between the head groups and the monomer tails will decrease
  the stability of polar molecules near the head groups. Alternatively, one
  can focus on designing head groups with varying hydrogen bonding capabilities.
  One can increase the number of hydrogen bonding sites on the head groups
  in order to trap more solutes, or decrease the number of hydrogen bond sites
  to trap less. Finally, one can attempt to control the degree to which solutes
  coordinate with counterions. Changing the size and valence of the counter 
  ion may offer some interesting behavior.

  %BJC: future work? i.e. talk about mathematical modeling

  \section{Supporting Information}

  Detailed explanations and expansions upon the results and procedures mentioned in
  the main text are described in the Supporting Information. This information is
  available free of charge via the Internet at http://pubs.acs.org.

  \section{Acknowledgements}

  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  \clearpage

  \bibliographystyle{ieeetr}
  \bibliography{transport}

  \newpage

  \section{TOC Graphic}

\end{document}

### 2019-04-10 Ben_Manuscripts/comps/Outline.tex
Started paper for comprehensive exam

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage[x11names,table]{xcolor}
\renewcommand{\baselinestretch}{1.5}
\usepackage{url}
\newcommand{\foo}{\color{LightSteelBlue3}\makebox[0pt]{\textbullet}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}
\DeclareCaptionFont{blue}{\color{LightSteelBlue3}}
\usepackage{array,booktabs}

\title{PhD Research Proposal: Molecular Level Design of Nanoporous Lyotropic Liquid
Crystal Membranes for Aqueous Separations \\ \vspace{0.5cm}
\large Advisors: Michael Shirts and Richard Noble}

\author{Benjamin J. Coscia}

\begin{document}

  \maketitle
  \thispagestyle{empty}
  \clearpage
  \setcounter{page}{1} % don't count title page as a page

  \section{State of the Art}\label{section:state-of-the-art}

  \subsection*{Commercial Membranes for Small Molecule Separations}

  % perhaps a word or two about micro and ultra filtration

  % re-word. This paragraph is verbatim from structure paper
  More highly selective nanoporous membranes would be extremely useful
  in performing complex aqueous separations with seawater and various
  types of wastewater.
  \begin{itemize}
    \item For example, Sodium chloride and boron in seawater 
    \cite{fritzmann_state---art_2007} and organic micropollutants found in
    municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
    represent just a few of the diverse contaminants of water sources. 
    \item By efficiently separating contaminants from feed solutions with
    highly selective membranes, it is possible to reduce the number of 
    required membrane passes and post-treatment steps needed for a given 
    filtration process \cite{werber_materials_2016}, thus lowering energy
    requirements. 
    \item Additionally, one can also extract valuable resources from the 
    feed streams. For example, flowback water produced during hydraulic
    fracturing of shale formations contains dissolved species such as acetate
    whose extraction has economic value \cite{dischinger_application_2017}.
  \end{itemize}

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
  filtration processes that can be used to separate solutes on the order of
  1 nm in size and smaller, including ions.
  \begin{itemize}  
    \item Both apply hydraulic pressure to the feed solution in order to 
    overcome osmotic pressure and force water and unfiltered components 
    through the membrane.
    \item RO membranes are typically thin film composite with a porous mechanical 
    support layer and a thin but dense polymer matrix active layer where separations
    occur.\cite{jeong_interfacial_2007}
    \item RO separates solutes based on the solute's ability to dissolve into
    and diffuse through the tortuous pathways available in dense active layer.
    \item RO offers high selectivity at the cost of relatively high energy 
    requirements since one must apply a large hydraulic pressure in order to 
    achieve an economical flux.  % get number
    \item In contrast to RO membranes, NF membranes have explicit pores on the
    order of 1 nm in size. 
    \item Typically, separations are achieved based on size exclusion and
    charge exclusion if the membrane surface is charged.
    \item NF membranes require significantly less applied pressure in order
    to achieve solute flux comparable to RO.
    \item Unfortunately, conventional synthesis processes, such as 
    phase-inversion\cite{smolders_microstructures_1992} are stochastic in
    nature which yields pores that are polydisperse in size.\cite{werber_materials_2016} % name some synthesis processes
    \item Pore size polydispersity is detrimental to membrane selectivity
  \end{itemize}

  The downfall of RO and NF membranes can be summarized by the well-known
  permeability-selectivity tradeoff. Namely, it is difficult to increase the
  permeability of a desired molecular or atomic species, while maintaining
  the same retention of an undesired species.\cite{werber_materials_2016}

  \subsection*{Nanostructured Membranes}

  Nanostructured membranes attempt to overcome the permeability-selectivity 
  tradeoff through molecular level design.
  \begin{itemize}
	\item Graphene sheets, carbon nanotubes (CNTs) and zeolites are three
	highly studied nanostructured technologies.
  \end{itemize}

  Graphene membranes are an extremely active are of research because 
  they offer potential for extremely high permeability membranes.
  \begin{itemize}
    \item 2D materials
    \item Functionalization?
    \item Easy to introduce defects
    \item Multi-layered
  \end{itemize}

  Carbon nanotubes have shown promise due to unprecedentedly fast
  water transport. 
  \begin{itemize}
    \item Functionalization of nanotubes
    \item Aligned nanotubes difficult to synthesize
  \end{itemize}

  Zeolite-coated ceramic membranes offer the potential for permeabilities
  comparable to ultrafiltration with selectivities as good as NF and RO. 
  \begin{itemize}
    \item Zeolites have highly uniform nm-sized crystalline structures with
    cage-like cavities that allow movement and trapping of small solutes. \cite{pendergast_review_2011}
    \item The crystalline frameworks are typically formed by networks of silicon
    and aluminum each attached to 4 oxygen atoms in a tetrahedral arrangement. 
    \item One can replace the silicon and aluminum atoms via ion exchange 
    in order to control the size of the cavities and hence its molecular-seiving properties.
    \item A number of studies have tested the permeability and sodium salt
    rejection of various zeolite membranes, however none have fully
    overcome the permeability-selectivity tradeoff.
    \item Most are prone to defects in the crystalline structure.
  \end{itemize}

  \subsection*{Lyotropic Liquid Crystal Membranes}

  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
  (LLC) membranes can be produced at moderate scale and may be capable of 
  performing highly selective separations. 
  \begin{itemize}  
    \item LLCs are amphiphilic molecules that have the ability to self-assemble
    into porous nanostructures \cite{smith_ordered_1997} and can be cross-linked
    to create mechanically strong membrane films with periodic pores on the
    order of 1 nm in diameter \cite{zhou_supported_2005}. 
    \item LLC membrane pores are uniform in size because they are formed by 
    self-assembly. 
    \item Since LLC polymer membranes lack an appreciable pore size distribution,
    they inherently exhibit high selectivity due to their strict molecular weight
    cut-off (MWCO)~\cite{zhou_supported_2005}. 
    \item Additionally, LLC monomers can be salts, and therefore lead to Donnan
    exclusion of ions in solution.\cite{donnan_theory_1995}
%    The membrane gains a net surface charge when counterions from
%  the head groups that line the pore walls escape into the feed solution in an
%  effort to balance the gradients of concentration and electric potential
%  \cite{donnan_theory_1995}.
  \end{itemize}

  The feasibility of nanostructured LLC polymer membranes for selective separations
  has been demonstrated using LLC monomers that form the type 1 bicontinuous cubic
  (Q\textsubscript{I})\cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
  phases. 
  \begin{itemize}
    \item When separating organic solutes from NaCl, Q\textsubscript{I}-phase
    membrane filtration experiments have shown selectivity 2--3 times higher than
    commercial RO and 6--12 times higher than commercial NF membranes.\cite{dischinger_application_2017}
    \item When separating a series of various sized dyes, the 
    H\textsubscript{II}-phase membrane showed complete rejection of dyes bigger
    than 1.2 nm in size \cite{zhou_supported_2005}.
  \end{itemize}

  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:assembly}) has a
  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
  \begin{itemize}
	  \item The H\textsubscript{II} phase forms at room temperature in the 
	  presence of ca.~10 wt\% water and consists of hexagonally packed, 
	  hydrophilic pore columns\cite{smith_ordered_1997}. 
	  % BJC: should rethink the following since we think that thermotropic doesn't exist
	  \item In the absence of water, neat monomer will form the same hexagonal
	  columnar structure which, in the literature, has been referred to as the
	  Col\textsubscript{h} thermotropic phase\cite{feng_scalable_2014}.
  \end{itemize}

  Q\textsubscript{I}-phase membranes consist of a tortuous network of three
  dimensionally interconnected pores that prevent optimal through-plane
  transport. 
  \begin{itemize}
    \item In contrast, the densely packed, non-tortuous and uniform sized
    pores of H\textsubscript{II}-phase membranes represent the ideal geometry
    for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.  
    \item However, the hexagonally packed LC domains of the H\textsubscript{II}-phase
    generally form mutually unaligned domains, which hurts membrane permeability. 
    \item This domain scale misalignment had inhibited further development of 
    this technology, and research efforts were focused on the Q\textsubscript{I}
    phase, whose geometry does not require alignment~\cite{zhou_new_2007}.
  \end{itemize}

  Recently, researchers have learned how to macroscopically align the
  hexagonal domains which has revived research into H\textsubscript{II}-phase LLC
  polymer membranes. 
  \begin{itemize}
    \item In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
    domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
	with subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
	\item In 2016, Feng et al.~showed that one could also obtain the same result
	by confining the neat monomer between PDMS or glass substrates since hexagonal
	mesophases preferentially anchor perpendicular to both surfaces\cite{feng_thin_2016}.
  \end{itemize}

  Unfortunately, reproducing the work of Feng et al. with the H\textsubscript{II}
  has been an experimental challenge. Therefore, the primary focus of experimental
  research efforts has been with the Q\textsubscript{I} phase.

  \section{Project Objectives}\label{section:objectives}

  Our current understanding of the molecular details of LLC membranes'
  nanostructure is not sufficient to be able to precisely design them for
  specific separations. 
  \begin{itemize} 
%    \item Over the past 20 years, H\textsubscript{II}-phase LLC polymer 
%    membrane studies have been limited primarily to the Na-GA3C11 monomer
%    with some characterization done after minor structural modifications.\cite{zhou_supported_2005,resel_structural_2000}
    \item Dischinger et al.~attempted to use an empirical model
    that correlates the physiochemical properties of the counterion used in
    a Q\textsubscript{I}-phase LLC membrane to solute rejection.\cite{dischinger_effect_2017}
    \item Although their model showed some qualitative agreement with experiment, the
    quality of fit of their model was limited due to complex solute-membrane
    interactions that could not easily be modeled. 
  \end{itemize}

  A molecular-level understanding of structure of and transport in LLC polymer 
  membranes, enabled by molecular dynamics (MD) simulations, can provide 
  guidelines to reduce the large chemical space available to design
  monomers for creation of separation-specific membranes. 
  \begin{itemize}
    \item Using a sufficiently accurate molecular model, we can directly 
    observe transport of solutes within LLC membrane nanopores and infer
    mechanisms. 
    \item Based on this information we can intelligently design new membranes
    by screening new liquid crystal monomer designs.
    \item Our most promising designs can be tested experimentally.
  \end{itemize}

  \noindent There are five primary objectives of our work.
  \begin{enumerate}

    \item Develop techniques to build and understand the nanoscopic structure
    of LLC membranes.

    Useful molecular-level modeling should incorporate a detailed picture 
    of the nanoscopic pore structure, which is crucial to understanding
    the role of monomer structure in solute transport and membrane design.
    We will generate simulated X-ray diffraction patterns from MD trajectories
    and compare them to an experimental 2D wide angle X-ray scattering (WAXS)
    spectrum of a Col\textsubscript{h} phase membrane. We will assess the extent
    to which we can apply our understanding to the H\textsubscript{II} phase,
    as well as systems built with alternate monomers.

    \item Determine dominant solute-membrane interactions that give rise to
    transport mechanisms.

    We will observe transport of a relatively large set of small polar solutes
    placed within the H\textsubscript{II} membrane nanopores. We will observe
    the time series of each solute's position as well as directly measure the
    physical interactions, such as hydrogen bonding and ion coordination, 
    between solutes and LLC monomers.

    \item Create a stochastic model which can project long timescale 
    transport behavior.

    We will combine our general knowledge of the solute transport mechanisms
    with simulation data in order to inform a stochastic model. This model
    should closely reproduce the time series that we observe in our simulations.
    Due to the low computational cost of a stochastic model relative to 
    MD simulations, we will be able to project long timescale transport behavior
    and make well-converged predictions of macroscopic transport properties.

    \item Adapt the same analysis to the Q\textsubscript{I} phase.

    Over the course of this project, experimental research surrounding
    LLC membranes has shifted nearly all focus towards the Q\textsubscript{I}
    phase due to its more facile synthesis.	Although most of our work has 
    been applied to the H\textsubscript{II} phase, we expect that much of 
    the same analyses can be applied to the Q\textsubscript{I} phase. The 
    biggest challenge will be adapting our techniques to its more complex
    geometry.

    \item Enable easy continuation of our work with a dedicated and 
    well-documented python package.

	Although molecular simulations have become popular
	for studying systems at the atomic level, LLCs used in this context
	have not been heavily investigated. Consequently, much of the 
	analysis developed for this project is not widely applied. Therefore, 
	it is important for us to make available the scripts that reproduce
	the exact results presented in our published papers along with detailed
	documentation of the scripts. This will ensure near-seamless continuation
	of this project and accelerate the development of LLC membranes.

  \end{enumerate}

  \section{Progress to Date}\label{section:progress}

  \textbf{\large Objective 1:} \textit{\large Build and understand nanoscopic structure of LLC membranes} (\textcolor{green!40!olive}{\textbf{Complete}})

  \noindent We have developed a procedure for building an LLC membrane unit cell.

  \noindent We have created a molecular model that is maximally consistent with
  experimental WAXS data.

  \noindent Water is necessary to fully reproduce all features in the WAXS pattern.

  \noindent An ensemble of simulation trajectories best capture the system's 
  time averaged behavior.

  \noindent \textbf{\large Objective 2:} \textit{\large Determine transport mechanisms} (\textcolor{green!40!olive}{\textbf{Complete}})

  \noindent We added additional water to our model to create the H\textsubscript{II} phase

  \noindent Water partitions into the distal tail region

  \noindent The pore structure changes

  \noindent We place 20 small polar solutes

  \noindent The mean squared displacements are not a monotonic function of solute MSD

  \noindent Solute behavior is subdiffusive.

  \noindent Subdiffusive behavior is a consequence of a hopping and trapping mechanism.

  \noindent There are three mechanisms of entrapment.

  \noindent \textbf{\large Objective 3:} \textit{\large Create a stochastic model} (\textcolor{blue}{\textbf{In Progress}})

  \noindent We are in the process of developing the theory required to build a 
  stochastic model.

  \noindent The distribution of dwell times is power law distributed.

  \noindent The distribution of hop lengths is approximately gaussian

  \noindent The model will likely have a radial dependence.

  \noindent \textbf{\large Objective 4:} \textit{\large Apply analyses to Q\textsubscript{I} phase} (\textcolor{blue}{\textbf{In Progress}})

  \noindent We have developed a procedure to build the Q\textsubscript{I} phase.

  \noindent \textbf{\large Objective 5} \textit{\large Create a well-documented python package} (\textcolor{blue}{\textbf{In Progress}})

  Python scripts used to simulate X-ray diffraction patterns are available in the following
  GitHub repository: \url{https://github.com/joeyelk/MD-Structure-Factor}. Documentation
  is forthcoming.

  Python scripts used to conduct all other post-simulation trajectory analysis are 
  also available on GitHub: \url{https://github.com/shirtsgroup/LLC_Membranes}. 
  Documentation is a work in progress. It is available for viewing in its 
  current state at \url{https://llc-membranes.readthedocs.io/en/latest/}.

  \section{Timeline for Completion of Objectives}\label{section:timeline}

  A schematic of the estimated timeline that will be followed for the completion of
  tasks pertinent to finishing all objectives is given in Table~\ref{table:timeline}.
  \begin{itemize}
    \item Simulations required to study the structure of the bicontinuous cubic
    phase will be run in parallel while working out the details of our stochastic
    model of transport in the H\textsubscript{II} phase.
    \item Simulations and analysis required for Q\textsubscript{I} phase solute 
    transport studies analogous to those of Objective 2 will be carried out 
    throughout Fall 2019.
    \item Finalization of code documentation and application of a stochastic
    model to the Q\textsubscript{I} phase will be finished by May 2020
  \end{itemize}

  \begin{center}  
  \begin{table}[!htb]
	\renewcommand\arraystretch{1.4}\arrayrulecolor{LightSteelBlue3}
	\captionsetup{singlelinecheck=false, font=blue, labelfont=sc, labelsep=quad}
	\caption{Estimated Timeline for Completion of Objectives}\vskip -1.5ex
	\begin{tabular}{@{\,}r <{\hskip 2pt} !{\foo} >{\raggedright\arraybackslash}p{8cm}}
	\toprule
	\addlinespace[1.5ex]
	August 2019 & Complete Stochastic Model for H\textsubscript{II} phase \\
	September 2019 & Finalize Q\textsubscript{I} phase structure \\
    January 2020 & Finish transport study of Q\textsubscript{I} phase \\
    April 2020 & Complete code documentation \\
    April 2020 & Finish application of stochastic model to Q\textsubscript{I} phase \\
    May 2020 & PhD Defense \\
	\end{tabular}
	\label{table:timeline}
  \end{table}
  \end{center}

  \section{Resource Requirements}\label{section:resources}
  %BJC: Not sure what to include here. Hour estimate? Or omit this section.

  The remainder of our work will require the use of high performance computing (HPC)
  resources. 
  \begin{itemize}
    \item We will continue using Bridges, an XSEDE resource as well as Summit, a
    supercomputer located at CU Boulder.
  \end{itemize}

  % BJC: add funding?

  \newpage
  \bibliographystyle{ieeetr}
  \bibliography{comps}

\end{document}

### 2019-04-11 Ben_Manuscripts/comps/Outline.tex
Fixed up abstracts, filled in Objective 1 and 2 progress

@@
 \usepackage[x11names,table]{xcolor}
-\renewcommand{\baselinestretch}{1.5}
+\usepackage{setspace}
+\usepackage[font=small]{caption}
+\setstretch{1.5} % line spacing
+\captionsetup[table]{font={stretch=1,small}} % line spacing in tables
+\captionsetup[figure]{font={stretch=1,small}} % line spacing in figures
 \usepackage{url}
+% For timeline
 \newcommand{\foo}{\color{LightSteelBlue3}\makebox[0pt]{\textbullet}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}
@@
 \begin{document}
+
+  \graphicspath{{./figures/}}
 
@@
 
-  \textbf{\large Objective 1:} \textit{\large Build and understand nanoscopic structure of LLC membranes} (\textcolor{green!40!olive}{\textbf{Complete}})
+  \textbf{\large Objective 1:} {\large Build and understand the nanoscopic structure of LLC membranes} (\textcolor{green!40!olive}{\textbf{Complete}})
 
-  \noindent We have developed a procedure for building an LLC membrane unit cell.
+  \noindent Our first task was to develop a procedure for building and equilibrating 
+  an atomistic LLC membrane system (see Figure~\ref{fig:assembly}).
+  \begin{itemize}
+    \item We built a monoclinic unit cell consisting of four pores.
+    \item Each pore is composed of monomer columns, where each column
+    consists of 20 monomers stacked on top of each other so that the 
+    phenyl groups are coplanar with each other and the $xy$ plane. 
+    \item The columns are oriented so that the hydrophilic monomer head
+    groups face towards the pore center.
+    \item We equilibrate the unit cell using a series of simulations
+    with head groups held in place by position restraints. 
+    \item We gradually reduce the force constant of the position 
+    restraints until the system is completely unrestrained.
+    \item We carried out 400 ns equilibration simulations.
+  \end{itemize}
 
-  \noindent We have created a molecular model that is maximally consistent with
-  experimental WAXS data.
+  \begin{figure}[!htb]
+      \centering
+      \begin{subfigure}{.3\textwidth}
+              \centering
+              \includegraphics[width=\textwidth]{NaGA3C11.pdf}
+              \caption{}~\label{fig:monomer}
+      \end{subfigure}
+      \begin{subfigure}{.3\textwidth}
+              \centering
+              \includegraphics[width=\textwidth]{monomer_twocolor.pdf}
+              \caption{}~\label{fig:atomistic_monomer}
+      \end{subfigure}
+      \begin{subfigure}{0.3\linewidth}
+              \centering
+              \includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
+              \caption{}~\label{fig:wedge}
+      \end{subfigure}
+              \begin{subfigure}{0.4\linewidth}
+              \centering
+              \includegraphics[width=0.6\textwidth]{columns.pdf}
+              \caption{}~\label{fig:wedge_layer}
+      \end{subfigure}
+      \begin{subfigure}{0.4\linewidth}
+              \centering
+              \includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
+              \caption{}~\label{fig:hex_packing_simple}
+      \end{subfigure}
+      \caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
+      exhibits wedge-like character. (d) Monomers stack on top of each other to
+      create columns with short range order, then assemble into pores with
+      hydrophilic head groups (blue) facing towards the pore center. (e) The
+      pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
+  \end{figure}
 
-  \noindent Water is necessary to fully reproduce all features in the WAXS pattern.
+  \noindent We tested a number of different initial column architectures. 
+  \begin{itemize}
+      \item We stacked monomers in parallel displaced and sandwiched 
+      configurations, two possible $\pi$-$\pi$ stacking modes.
+      \item We also varied the initial distance between stacked monomers, $d$.
+      \item We chose values of 3.7 \AA, based on experimental WAXS 
+      measurements, as well as 5 \AA as a test of its sensitivity.
+  \end{itemize}
 
-  \noindent An ensemble of simulation trajectories best capture the system's 
-  time averaged behavior.
+  \noindent Our model's geometry is most consistent with experiment for systems
+  built with 5 columns per pore and monomers initially stacked 3.7 \AA apart
+  (see Figure~\ref{fig:p2p}). 
+  \begin{itemize}
+    \item We equilibrated systems with 4, 5, 6, 7 and 8 columns per pore.
+    \item The pore spacing of 5 column-per-pore systems agree well with experiment.
+    \item 6 column-per-pore systems built with $d$ = 5 \AA appear to yield an
+    experimentally consistent pore spacing however, the equilibrated distance
+    between stacked monomers stay close to 5 \AA which is inconsistent with 
+    experiment. 
+    \item In general, the equilibrated distance between monomers stays close to
+    its initial value. 
+  \end{itemize}
+
+  \begin{figure}[!htb]
+    \centering
+    \includegraphics[width=\linewidth]{p2p.pdf}
+    \caption{Systems with 5 columns per pore have equilibrated pore spacings
+            closest to the experimental value of 4.12 nm. The equilibrated 
+            pore spacing of the model increases as the number of columns in
+            each pore increases.}~\label{fig:p2p}
+  \end{figure}
+
+%  \noindent On timescales that we can reasonably simulate, our equilibrated
+%  structures show some initial configuration dependence. 
+%  \begin{itemize}
+%    \item All of the systems used to generate Figure~\ref{fig:p2p} are at 
+%    least metastable.
+%    \item We observe no large scale rearrangements that would be necessary
+%    for all structures to converge to the same equilibrium structure. 
+%  \end{itemize}
+
+  \noindent We further validated the structure of our molecular model by 
+  verifying its consistency with five major reflections present in the 
+  experimental WAXS pattern.
+  \begin{itemize}
+    \item The five major reflections and the structural features leading
+    to them are summarized in Figure~\ref{fig:WAXS_comparison}.
+    \item Using MD trajectories, we simulated X-ray diffraction (XRD) 
+    patterns that we could compare to the WAXS data by taking the 
+    appropriate cross-section of the time-averaged 3D structure factor. 
+    \item None of the models simulated to this point could reproduce R-double.   
+  \end{itemize}
+
+  \noindent It is necessary to add a small amount of water to our model in
+  order to fully reproduce all features of the WAXS pattern.
+  \begin{itemize}
+    \item We built our most experimentally consistent structure in the 
+    parallel displaced configuration with 1 wt \% water added to the 
+    pores. 
+    \item This is the only configuration that gives rise to the 
+    R-double feature. 
+    \item R-double appears because vertically adjacent monomer head groups
+    hydrogen bond with shared water molecules, causing them to be drawn 
+    closer together.
+    \item When multiple pairing interactions occur in series along the 
+    same pore axis, the center of masses of the pairs are spaced apart at 
+    twice the $\pi$-stacking distance. 
+  \end{itemize}
+
+  %\begin{wrapfigure}{L}{0.5\textwidth}
+  \begin{figure}[!htb]
+  	\centering
+    \begin{subfigure}{0.49\linewidth}
+    	\includegraphics[width=\linewidth]{WAXS_annotated_words.pdf}
+        \caption{Experiment}\label{fig:WAXS}
+    \end{subfigure}
+	\begin{subfigure}{0.49\linewidth}
+        \includegraphics[width=\linewidth]{solvated_offset_rzplot_1.pdf}
+        \caption{Simulation}\label{fig:solvated_XRD}   
+	\end{subfigure}
+    \caption{(a) 2D-WAXS gives details about repeating features on the order of
+    angstroms. Our explanations for each of the 5 major reflections present are
+    as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack 3.7 \AA~apart. 
+    (R-double) Monomer head groups associate into pairs by hydrogen bonding with
+    a shared water molecule. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. 
+    (R-spots) Monomer tails pack hexagonally. (R-pores) The pores are spaced 
+    4.12 nm apart and pack hexagonally. (b) We obtain a maximally consistent
+    match between simulated XRD patterns and experimental WAXS data when we
+    build systems in the parallel displaced configuration with 1 wt \% water
+    included in the pores.}\label{fig:WAXS_comparison}
+ \end{figure}
+ %\end{wrapfigure}
+
+  %BJC: I think this is important to say somewhere
+  \noindent On the timescales that we can reasonably simulate, our model
+  exhibits slow dynamics. 
+  \begin{itemize}
+    \item Consequently, there are very few uncorrelated frames in our 
+    trajectories which leads to noise in the simulated XRD patterns. 
+    \item We can overcome this issue by combining the structure factors
+    generated from an ensemble of trajectories produced starting from 
+    an ensemble of uncorrelated initial configurations.
+  \end{itemize}
+
+  \noindent The composition of the pores does not change regardless of which
+  initial configuration we study.
+  \begin{itemize}
+    \item In Figure~\ref{fig:overlaid_densities}, we plot the radial density
+    of various monomer components as a function of distance from the pore
+    centers. 
+    \item All are qualitatively similar meaning that a solute placed in 
+    any of these systems should experience a similar chemical environment.
+    \item Although we will move forward with our most promising configuration,
+    this is an important finding since it implies that we do not need to apply
+    the same level of rigor when screening new monomers.
+  \end{itemize}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{regional_density_legend.pdf}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{head_group_density.pdf}
+        \caption{Head Groups}
+        \label{fig:head_groups_regional_density}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{tails_density.pdf}
+        \caption{Tails}
+        \label{fig:tails_regional_density}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+        \includegraphics[width=1\linewidth]{sodium_density.pdf}
+        \caption{Sodium Ions}
+        \label{fig:sodium_regional_density}
+  \end{subfigure}
+  \caption{In all cases, the component radial distribution functions are similar.
+      They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
+          regions. The biggest differences are at r=0 where noise is higher due to
+          decreased sampling. The center of the pore is not hollow, but contains sodium ions and
+          head groups, even when the system is solvated. This architecture may impede transport in
+          the real system in a chemically-dependent manner.
+          The solvated system has a lower density of head groups near the
+          pore center which is likely due to the swelling that is necessary in order to fit water
+          molecules in the pore region.}~\label{fig:overlaid_densities}
+  \end{figure}
 
@@
 
-  \noindent We added additional water to our model to create the H\textsubscript{II} phase
+  \noindent We added additional water to our best Col\textsubscript{h} 
+  phase model in order to create the H\textsubscript{II} phase.
+  \begin{itemize}
+    \item There have been a range of reported water contents used to 
+    form the H\textsubscript{II} phase with this particular monomer.
+    \item Although Resel et al. commented that the system is likely
+    already fully hydrated at 7 wt \% water with additional water
+    trapped in defects between mesophases.
+    \item Therefore, we built two systems with 5 and 10 wt \% water.
+  \end{itemize}
 
-  \noindent Water partitions into the distal tail region
+  \noindent We observed that water partitions into the distal tail region.
+  \begin{itemize}
+    \item We define the distal tail region to be any radial distance 
+    greater than 1.5 nm from any pore center. 
+    \item There is an approximately 3:2 ratio of water in the pores to
+    water in the distal tails. 
+    \item Due to the wedge shape of the monomers, the distal tail region
+    has a relatively low density leaving space for water molecules to 
+    fill.  
+  \end{itemize}
 
-  \noindent The pore structure changes
+  \noindent The pores of the H\textsubscript{II} phase are primarily a 
+  mixture of water and sodium ions.
+  \begin{itemize}
+    \item The maximum density of head groups occurs 0.45 and 0.65 nm from
+    the pore center in the 5 and 10 wt\% water systems respectively (see
+    Figure~\ref{fig:component_densities}). 
+    \item There are almost no head groups occupying the pore center.
+  \end{itemize}
 
-  \noindent We place 20 small polar solutes
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{component_density_dry.pdf}
+  %BJC: simulation is extended to smooth out these curves
+  \caption{Dry System}\label{fig:component_density_dry}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \vspace{-0.5cm}
+  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
+  \label{fig:monomer_color_coded}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
+  \caption{5 wt\% water}\label{fig:component_density_5wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
+  \caption{10 wt\% water}\label{fig:component_density_10wt}
+  \end{subfigure}
+  \caption{The radial densities of various monomer components paint a
+  picture of the pore topology where the pore centers are primarily composed
+  of water and sodium ions. The monomer groups labeled in each plot correspond to
+  the color-coded monomer pictured in the upper right corner of the figure.
+  All RDFs represent the number of atoms located at a given distance from the
+  pore center normalized by the volume of the annular bin to which they belong.
+  (a) In the dry system, the density of head groups and sodium ions are highest
+  within 0.25 nm of the pore center. (b) In the 5 wt \% system, monomer head
+  groups retreat about 0.2 nm radially in order to make room for water molecules.
+  (c) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
+  for more water.}\label{fig:component_densities}
+  \end{figure}
 
-  \noindent The mean squared displacements are not a monotonic function of solute MSD
+  \noindent Water and sodium transport is significantly faster in the less
+  crowded 10 wt \% water pores. 
+  \begin{itemize}
+    \item The MSD of water is about 51 times higher and the MSD of sodium is
+    about 49 times higher compared to 5 wt \% system.
+    \item In general we observe similar solute transport mechanisms in the 5
+    and 10 wt \% water systems but at different time scales.
+    \item Therefore, we will focus on the 10 wt \% water system since we
+    can collect a larger quantity of mechanistic data from the solute 
+    trajectories.
+  \end{itemize}
 
-  \noindent Solute behavior is subdiffusive.
+  \noindent We observed transport of 20 different small polar solutes in the
+  pores of our model. 
+  \begin{itemize}
+    \item We created a separate initial configuration for each solute studied.
+    \item We placed 6 solutes, equally spaced in $z$, in each nanopore.
+    \item We allowed the solutes to simulate for 1 microsecond. 
+  \end{itemize}
 
-  \noindent Subdiffusive behavior is a consequence of a hopping and trapping mechanism.
+  \noindent The MSDs are not a monotonic function of solute size.
+  \begin{itemize}
+    \item In Figure~\ref{fig:all_msds_10wt}, we plotted the average
+    MSD of each solute. 
+    \item In Figure~\ref{fig:msd_radius_10wt}, we plotted solute
+    MSDs against their molecular radius.
+    \item We also plotted theoretical curves which illustrate the 
+    expected MSD of each solute if they were to travel unhindered.
+    \item We ensured that the Stokes-Einstein equation with the
+    correction factor of Gierer and Wirtz passed through methanol 
+    in order to give an approximate frame of reference. 
+    \item Methanol is small and therefore can travel relatively
+    unhindered compared to all other solutes.
+    \item The theoretical line can be used as an approximate boundary
+    between subdiffusive, Brownian and superdiffusive behavior.
+  \end{itemize}
 
-  \noindent There are three mechanisms of entrapment.
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
+  \caption{10 wt \% water}\label{fig:all_msds_10wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf}
+  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
+  \end{subfigure}
+  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
+  smaller than those of the solutes in the 10 wt \% water system (b). The
+  MSDs are not a monotonic function of molecular size (c and d). A significant
+  number of solute MSDs fall below the theoretical lines predicted by the
+  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
+  }\label{fig:msds}
+  \end{figure}
+
+% 5 and 10 wt %
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
+%  \caption{5 wt \% water}\label{fig:all_msds_5wt}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
+%  \caption{10 wt \% water}\label{fig:all_msds_10wt}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf}
+%  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf}
+%  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
+%  \end{subfigure}
+%  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
+%  smaller than those of the solutes in the 10 wt \% water system (b). The
+%  MSDs are not a monotonic function of molecular size (c and d). A significant
+%  number of solute MSDs fall below the theoretical lines predicted by the
+%  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
+%  }\label{fig:msds}
+%  \end{figure}
+
+  \noindent Intermittent hops between long periods of entrapment lead
+  to subdiffusive solute transport behavior. 
+  \begin{itemize}
+    \item As Figure~\ref{fig:msd_radius_10wt} implies, most solutes
+    move significantly slower than expected.
+    \item In Figure~\ref{fig:example_ztraces}, we've plotted the $z$-direction
+    trajectory of three ethanol molecules.
+    \item Typically, long periods of entrapment occur when ethanol 
+    molecules are far from the pore center, while there is a much 
+    greater degree of mobility close to the pore center.
+    \item The MSD curve averaged over all ethanol trajectories is shown
+    in Figure~\ref{fig:example_msd}.
+    \item The curve is sub-linear and thus subdiffusive.
+  \end{itemize}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
+  \caption{}\label{fig:example_ztraces}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\linewidth]{example_msd.pdf}
+  \caption{}\label{fig:example_msd}
+  \end{subfigure}
+  \caption{All solutes show subdiffusive transport behavior inside the membrane's
+  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
+  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
+  In general, the longest dwell times occur when solutes are situated far from the
+  pore center and the hops occur when solutes are close to the pore center. (b) The
+  time-averaged MSD of ethanol is sub-linear which suggests transport is governed
+  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
+  \end{figure}
+
+  \noindent We observe three mechanisms of entrapment that are responsible for 
+  subdiffusive behavior.
+  \begin{enumerate}
+    \item As already demonstrated in Figure~\ref{fig:example_ztraces}, solutes that
+    drift away from the pore center can become entangled in the monomer tails. 
+    \item Many of the solutes we studied are capable of donating hydrogen bonds to
+    monomer head groups and thus are prone to temporary immobilization through this interaction.
+    \item Because all solutes are polar, they have regions of concentrated electron
+    density, modeled as partial charges, which can associate with sodium ions
+    partially bound to monomer head groups.
+  \end{enumerate}
+
+  Due to the crowded environment among the monomer tails, solutes generally move faster
+  in the less dense pore region.
+  \begin{itemize}
+    \item Figure~\ref{fig:hop_lengths} shows that this is the case for all solutes.
+    \item Hops made in the pore region are on average 45 \% larger than those made
+    outside the pore region.
+  \end{itemize}
+
+  However, time spent in the pore region does not necessarily result
+  in a high MSD. 
+  \begin{itemize}
+    \item For example, ribose spends the largest fraction of time in 
+    the pore center, but has the lowest hop frequency and the third 
+    lowest average MSD (see Figures~\ref{fig:frac_time} and ~\ref{fig:hopfreq}).
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\linewidth]{hop_length.pdf}
+  \caption{}\label{fig:hop_lengths}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{frac_time_spent.pdf}
+  \caption{}\label{fig:frac_time}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{hopfreq_total.pdf}
+  \caption{}\label{fig:hopfreq}
+  \end{subfigure}
+  \caption{(a) Hops made in the pore region of the 10 wt \% water system
+  are, on average, 45 \% larger than those made outside the pore region.
+  The trend in hop lengths is similar to the trend in MSDs shown in
+  Figure~\ref{fig:all_msds_10wt} implying that solutes which make consistently
+  larger hops have higher MSDs. The fraction of time spent by a solute in the
+  pore region (b) does not necessarily lead to more frequent hopping (c). For
+  example, ribose spends the largest fraction of time in the pore region, yet
+  performs the the second lowest number of hops.}\label{fig:hops}
+  \end{figure}
+
+  \noindent The frequency with which solutes donate hydrogen bonds to monomer
+  head groups is related to the number of hydrogen bond donating atoms as well
+  as their identity.
+  \begin{itemize}
+    \item The percentage of solutes actively participating in at least one
+    hydrogen bond with a head group each frame descends as the number of 
+    hydroxyl groups decreases.
+    \item Solutes that containing sulfur and nitrogen atoms in place of 
+    oxygen atoms hydrogen bond less frequently since they are less 
+    electronegative elements.
+    \item The lifetime of hydrogen bonds follows nearly the same trend. Hydrogen
+    bonds of solutes that hydrogen bond more frequently last longer. 
+  \end{itemize}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{nhbonds_all.pdf}  % unique_hbonds.py
+  \caption{}\label{fig:nhbonds}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{hbond_lifetime.pdf}  % hbond_dwells.py
+  \caption{}\label{fig:hbond_dwells}
+  \end{subfigure}
+  \caption{(a) Solutes capable of donating hydrogen bonds to monomer head groups
+  do so to varying degrees. The reported percentages represent unique solute-monomer
+  hydrogen bonds. Individual solutes that hydrogen bond with multiple head groups
+  simultaneously are only counted once. (b) The lifetime of individual hydrogen
+  bonds appears correlated to the percentage of solutes involved in hydrogen bond
+  interactions. Hydrogen bond lifetimes tend to be longer for solutes that
+  hydrogen bond frequently. Note that solutes incapable of donating hydrogen
+  bonds are omitted from this figure.}\label{fig:hbonds}
+  \end{figure}
+
+  \noindent Solutes with carbonyl groups tend to associate with sodium ions most frequently.
+  \begin{itemize}
+    \item The seven solutes that coordinate to sodium the most and 
+    the six solutes with the longest association dwell times all contain 
+    carbonyl groups, with the exception of DMSO which has an analagous sulfinyl group
+    (see Figures~\ref{fig:all_solutes_NA_coordination} and~\ref{fig:all_NA_dwells}).
+	\item Solutes with nitrogen atoms adjacent to the carbonyl groups tend to
+	associate with sodium ions significantly more. 
+  \end{itemize}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{all_solutes_NA_coordination.pdf}
+  \caption{}\label{fig:all_solutes_NA_coordination}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{all_NA_dwells.pdf}
+  \caption{}\label{fig:all_NA_dwells}
+  \end{subfigure}
+  \caption{(a) Solutes, especially those with carbonyl groups, spend a
+  significant fraction of time coordinated to sodium ions. (b) The length
+  of time a solute-sodium pairs spends associated tends to be higher for
+  pairs that associate more frequently.}\label{fig:na_coordination}
+  \end{figure}
 
@@
 
-  \noindent The distribution of hop lengths is approximately gaussian
+  \noindent The distribution of hop lengths is approximately Gaussian
 
@@
 
-  \noindent We have developed a procedure to build the Q\textsubscript{I} phase.
+  Paralleling our work on the H\textsubscript{II} phase, our first task was to
+  build a suitable unit cell representation of the Q\textsubscript{I} phase. 
+  \begin{itemize}
+    \item Unfortunately, the true space group of the Q\textsubscript{I}
+    phase that we are studying is unknown. 
+    \item Experimental diffraction has narrowed down the possible bicontinuous
+    cubic configurations to the Ia3d and Pn3m space groups. 
+    \item Therefore, we will build both types of unit cells and search for
+    cues that can be used to differentiate them experimentally.
+  \end{itemize}
+
+  \noindent We have developed procedures to build both Ia3d and Pn3m unit
+  cells.
+  \begin{itemize}
+    \item To our knowledge, nobody has ever built an atomistic bicontinuous
+    cubic phase system without the aid of self-assembly.
+    \item Self-assembly can be a long process, especially for fully atomistic
+    systems. 
+    \item Instead, we used known analytical equations that describe the 
+    surface of these systems in order to place monomers into a unit cell.
+    \item Monomers are placed perpendicular to the surface in random locations
+    that don't overlap. One can control the pore size by translating monomers 
+    perpendicular to the surface at the point where they are attached.
+    %BJC: not sure how much more detail to include. Can go into a lot. Have to expand box and slowly compress. Add glycerol iteratively until there are no gaps.
+  \end{itemize}
 

### 2019-04-13 Ben_Manuscripts/transport/Draft.tex
Comments on abstract/intro.

@@
 
+%MRS2: ``dependent -> selective?'' 
 \title{Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
@@
 
+%MRS2: I think it would be useful to have a picture of the pores to
+% allow people to visualize what was going on.  ToC might be good, 
+% but I think that as people read, they need to see the 3D picture as well to think through things.
+
 \begin{document}
@@
   of water, sodium ions and 20 small polar solutes within the pores 
-  of an LLC membrane using atomistic molecular simulations. We found
+  of an LLC membrane using atomistic molecular simulations. We 
+  %MRS2: 
+  find
+  %found
+  %MRS2: ``transport rate -> transport''
   that the transport rate of a species is dependent not only on 
@@
   example, separation of salt from seawater or other briny sources can 
-  yield potable drinking water.\cite{fritzmann_state---art_2007} Removal
+  yield potable drinking water.~\cite{fritzmann_state---art_2007} Removal
   of organic micropollutants, such as personal care products, pesticides
   and pharmaceuticals, from surface and groundwaters, can have large benefits
-  for public health.\cite{schwarzenbach_challenge_2006} Finally,
+  for public health.~\cite{schwarzenbach_challenge_2006} Finally,
   one can purify and recover dissolved species present in complex
   hydraulic fracturing flowback water waste streams which would help mitigate
-  the effects of deep well injection and generate value.\cite{dischinger_application_2017} 
+  the effects of deep well injection and generate value.~\cite{dischinger_application_2017} 
   %BJC: could make last point more general
+  %MRS2: ``generate value'' is pretty vague, yeah.
 
@@
 %  capital investment needed to start the processes  
+% MRS2: maybe ``are possible'' -> ``are possible in part''?  Otherwise, it logically follows that they shouldn't have major drawbacks.
   All of these separations are possible with current commercial membrane
@@
   osmosis (RO) and nanofiltration (NF) dominate commercial membrane separations
-  of small molecules.\cite{warsinger_review_2018} RO membranes are typically
+  of small molecules.~\cite{warsinger_review_2018} RO membranes are typically
   dense polymer matrices that separate solutes based on differences in their
-  solubility and permeability in the membrane material.\cite{fritzmann_state---art_2007}
+  solubility and permeability in the membrane material.~\cite{fritzmann_state---art_2007}
   Although they can perform highly selective separations, high feed pressures,
   and thus large amounts of energy, are necessary in order to generate a 
-  useful permeate flux.\cite{van_der_bruggen_review_2003} NF membranes have 
+  useful permeate flux.~\cite{van_der_bruggen_review_2003} NF membranes have 
   well-defined nm-sized pores which can give the same permeate flux as RO
-  with lower applied pressure.\cite{hilal_comprehensive_2004} However, the 
-  pores are not uniform in size, limiting selectivity.\cite{werber_materials_2016}.
+  with lower applied pressure.~\cite{hilal_comprehensive_2004} However, the 
+  pores are not uniform in size, limiting selectivity.~\cite{werber_materials_2016}.
 %  Therefore, multiple membrane passes may be necessary in order to achieve 
@@
   selectivity of RO membranes while maintaining the high permeability
-  of NF membranes.\cite{zhou_supported_2005} The H\textsubscript{II} LLC
+  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} LLC
   phase is formed when LLC monomers self-assemble into hexagonally packed
-  and uniform-sized pores.\cite{smith_ordered_1997} Alignment and subsequent
+  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
   cross-linking of the hexagonal mesophases yields a mechanically strong
-  membrane.\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
+  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
   enforce a strict molecular-size cut-off while the hexagonal geometry is 
-  ideal for high permeability.\cite{zhou_supported_2005} Additionally, 
+  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
   because the LLC monomers are salts, Donnan exclusion plays a role in 
-  rejection of charged molecules upon pore entry.\cite{donnan_theory_1995}
+  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
 %  Zhou et al. demonstrated complete rejection
 %  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
-%  membranes.\cite{zhou_supported_2005}
+%  membranes.~\cite{zhou_supported_2005}
 
@@
   The functional LLC monomer head groups that occupy the pore region of the
-  membrane can interact with solutes. Dischinger et al. studied the 
+  membrane can interact with solutes. Dischinger et al.~studied the 
   performance of a Q\textsubscript{I} phase LLC membrane, which has a 
@@
   tortuous geometry, and observed a range of selectivities dependent on the
-  anion coordinated to the LLC monomer.\cite{dischinger_effect_2017} Intelligent 
+  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
   design of LLC monomers can help us tailor membranes for solute-specific
@@
   primarily characterized with size-exclusion experiments which emphasizes 
-  selectivity based on the ability to enter a given pore.\cite{zhou_supported_2005}
+  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
   While size-exclusion is a useful separation, it cannot reliably purify a 
@@
   important to take advantage of material properties other than pore size. 
-  Unfortunately, the complexity of LLC Membranes has obscured the interpretation
-  of experimental transport studies.\cite{dischinger_effect_2017}  % BJC: ref to Sarah?
-
+  %MRS2: is ``complexity'' the right word? Can we be more specific?
+  Unfortunately, the complexity of LLC membranes has obscured the interpretation
+  of experimental transport studies.~\cite{dischinger_effect_2017}  % BJC: ref to Sarah?
+
+  %MRS2: odd to have a one sentence paragraph?  MAyber just join with the next paragraph.
   Molecular dynamics (MD) simulations can give us mechanistic insights with 
@@
   structure of the hexagonal phase formed by the monomer Na-GA3C11, expanding 
-  upon the most recent experimental characterization.\cite{coscia_understanding_2018,feng_thin_2016}
+  upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
   We developed techniques for equilibrating the hexagonal phase formed by neat 
@@
 
+  %MRS2: can you put molecules in the table as well?
+I think it would be better for reference.
+Some of the larger ones may have small molecules.
+You can potentially partially stagger them horizontally so the size can be OK?
   \end{tcolorbox}
@@
 
-  First, we will comment on the membrane's structure. Previously, we have
+  %MRS2: generally, use present tense for what is being done in the paper, not future tense; 
+  %the paper is completely written, later sections are not being written in the future. 
+  %MRS2: descriptions of experiements can be in the past.   
+  %First, we will comment on the membrane's structure. 
+  We first address the structure of the pores formed in the membrane.
+  Previously, we have
   studied dry membrane systems and some systems with low water content. 
   We will observe how the radial density of monomer components and water 
-  change based on membrane water content.
+  change within the oore based on membrane water content.
 
@@
   % out of the pore. Maybe I can add some sort of chart. Need to think more.
-  Then we will present our efforts to understand how small molecules, 
+  % MRS2: it should be mentioned somewhere, probably worth a paragraph or so.  
+  % If WATER is much slower outside of the pores, everything else will be slow as well, so we can
+  % justify transport there not being interesting
+  %Then we will present 
+  We then present
+  our efforts to understand how small molecules, 
   including water, partition within the pores. From a macroscopic perspective,
@@
   necessarily stay confined to the centers of the pores or even within the 
-  pore region. We will study the gradient in composition of solutes and 
+  pore region. 
+  %MRS2:
+  %We will 
+  We then study the gradient in composition of solutes and 
   water and any resultant influence it might have on mechanistic properties.
-
-  Finally, and for the bulk of this work, we will present our observations 
+  %MRS2: tweak
+  %Finally, and for the bulk of this work, we will 
+  For the remainder of the paper, we 
+  present our observations 
   and explanations of the observed transport mechanisms exhibited by water
   and solutes. Given that the pores will restrict motion of the solutes, we
-  anticipate that transport will be hindered in some way. We want to understand
+  anticipate that transport will be hindered in some way.
+
+  %MRS2: next line is a statement about what we want to do, not what we did?
+  %We want to understand
+  We investigate
   the differences in solute motion, specifically its mean squared displacement 
@@
   using a broad range of water concentrations. In the literature, the system 
-  studied in this work is typically synthesized with close to 10 wt \% water.
+  studied in this work is typically synthesized with close to 10 wt\% water.
   \cite{smith_ordered_1997, zhou_new_2007} However, Resel et al. noted that the
-  system is likely fully hydrated with less than 7 wt \% water.\cite{resel_h2-phase_2000}
+  system is likely fully hydrated with less than 7 wt\% water.~\cite{resel_h2-phase_2000}
   Excess water fills space between hexagonal mesophases. We decided to test 
-  systems with two different water contents: 5 and 10 wt \%.
+  systems with two different water contents: 5 and 10 wt\%.
 
@@
   studying transport of water in the pores, we limited the calculations to water molecules
-  that spent greater than 95 \% of their time outside of the distal tail region.
+  that spent greater than 95\% of their time outside of the distal tail region.
 
@@
 
-  The $z$-direction MSD of water in the 10 wt \% system is linear. Therefore, for
+  The $z$-direction MSD of water in the 10 wt\% system is linear. Therefore, for
   the purpose of comparison, we calculated its diffusion constant by fitting a line
@@
   showed that the difference in diffusion constants of differently shaped 
-  particles, with constant molecular volume, did not differ by more than 25 \%
-  with most deviating by less than 10 \%.~\cite{chan_effects_2015}. 
+  particles, with constant molecular volume, did not differ by more than 25\%
+  with most deviating by less than 10\%.~\cite{chan_effects_2015}. 
   Third, we assume that the ratio of solute and solvent radii as calculated using the
@@
 
-  Using our procedure we found that sodium ions in a solution of tip3p water
+  Using our procedure we found that sodium ions in a solution of TIP3P water
   coordinate with an average of 3.6 water molecules. We created a 4 x 4 x 4
@@
   length of the unit cell in the $z$-direction. The average tortuosity
-  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt \%
+  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt\%
   water systems respectively.
@@
   group RDFs for each solute system in the plot. We generated 
-  95 \% confidence intervals by bootstrapping the RDF of each individual
+  95\% confidence intervals by bootstrapping the RDF of each individual
   head group. For each head group, we obtained an RDF averaged over the
@@
   In contrast to our previous work with a dry version of this 
-  membrane, the pore region of the 5 and 10 wt \% water 
+  membrane, the pore region of the 5 and 10 wt\% water 
   systems are primarily filled with water and sodium ions. We define the
@@
   carboxylate oxygen atoms. Figure~\ref{fig:component_densities} plots the RDF of each membrane
-  constituent in the dry system as well as the 5 and 10 wt \% water systems. 
+  constituent in the dry system as well as the 5 and 10 wt\% water systems. 
   In dry systems, the pore center is densely filled with sodium ions and head
@@
   pore. The density of sodium ions is somewhat uniform in the pore center of
-  the 5 wt \% water system while it shows a maximum closer to the head groups
-  in the 10 wt \% water system. The peak density of sodium ions is not at the
-  pore center in the 10 wt \% water system likely because they are still
+  the 5 wt\% water system while it shows a maximum closer to the head groups
+  in the 10 wt\% water system. The peak density of sodium ions is not at the
+  pore center in the 10 wt\% water system likely because they are still
   loosely associated with the monomer's carboxylate head groups.
@@
   \end{subfigure}
+  %MRS2: interesting that the head group max is near the transition point where water/tail groups 
   \caption{The radial densities of various monomer components paint a 
@@
   (a) In the dry system, the density of head groups and sodium ions are highest
-  within 0.25 nm of the pore center. (b) In the 5 wt \% system, monomer head 
+  within 0.25 nm of the pore center. (b) In the 5 wt\% system, monomer head 
   groups retreat about 0.2 nm radially in order to make room for water molecules.
-  (c) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
+  (c) Monomers in the 10 wt\% system retreat an additional 0.2 nm to make room
   for more water.}\label{fig:component_densities}
@@
   There is an appreciable amount of water that partitions into the distal tail
-  region of both systems. 28 \% and 31 \% of the total water is present in the tail
+  region of both systems. 28\% and 31\% of the total water is present in the tail
   regions of the 5 and 10 wt\% water systems respectively. See 
@@
   In the 10 wt\% water system, the MSD of water is about 51 times higher and
-  the MSD of sodium is about 49 times higher compared to the 5 wt \% water system. 
-  In the 10 wt \% water system, water moves about 51 times faster than sodium 
-  and in the 5 wt \% system, water moves about 49 times faster than sodium. Assuming
-  long timescale Brownian behavior of water in the 10 wt \% system, we measured its
-  diffusivity to be 7.45e-07 $cm^2 / s$ which is only 1.4 \% that of bulk tip3p 
+  the MSD of sodium is about 49 times higher compared to the 5 wt\% water system. 
+  In the 10 wt\% water system, water moves about 51 times faster than sodium 
+  and in the 5 wt\% system, water moves about 49 times faster than sodium. Assuming
+  long timescale Brownian behavior of water in the 10 wt\% system, we measured its
+  diffusivity to be $7.45 \times 10^{-7}$cm$^2$ / s which is only 1.4\% that of bulk TIP3P 
   water.~\cite{mahoney_diffusion_2000} %BJC: 7.45e-07 versus 5.19e-05 cm^2/s
@@
   \end{subfigure}
-  \caption{(a) The MSD of water in the 10 wt \% water system is about 51 times
-  higher than water in the 5 wt \% water system. (b) The MSD of sodium in the
-  10 wt \% water system is about 49 times higher than sodium in the 5 wt \% 
+  \caption{(a) The MSD of water in the 10 wt\% water system is about 51 times
+  higher than water in the 5 wt\% water system. (b) The MSD of sodium in the
+  10 wt\% water system is about 49 times higher than sodium in the 5 wt\% 
   water system.}\label{fig:msd_comparison}
@@
   Section~\ref{method:coordination}), sodium ions in our system, on average,
-  coordinate with about 1.7 water molecules in the 10 wt \% system and 1.2 water
+  coordinate with about 1.7 water molecules in the 10 wt\% system and 1.2 water
   molecules in the 5 wt\% system. However, the sodium ions are not undercoordinated
   since they frequently pair with negatively charged carboxylate head groups.
-  On average, sodium ions coordinate with 1 carboxylate group in the 10 wt \% water
-  system and 0.8 carboxylate groups in the 5 wt \% water system.
+  On average, sodium ions coordinate with 1 carboxylate group in the 10 wt\% water
+  system and 0.8 carboxylate groups in the 5 wt\% water system.
   % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
@@
   Like water and sodium above, the MSDs of the solutes studied in this work are 
-  significantly larger in the 10 wt \% system than those in the 5 wt \% water 
+  significantly larger in the 10 wt\% system than those in the 5 wt\% water 
   system (Figure~\ref{fig:msds}). The fastest moving solute in both cases, 
-  methanol, has an MSD about 175 times larger in the 10 wt \% versus the 5 wt 
+  methanol, has an MSD about 175 times larger in the 10 wt\% versus the 5 wt 
  \% water system. Clearly the equilibrium water content of a given LLC system will 
@@
   \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
-  \caption{5 wt \% water}\label{fig:all_msds_5wt}
+  \caption{5 wt\% water}\label{fig:all_msds_5wt}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
-  \caption{10 wt \% water}\label{fig:all_msds_10wt}
+  \caption{10 wt\% water}\label{fig:all_msds_10wt}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
-  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
+  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
-  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
-  \end{subfigure}
-  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
-  smaller than those of the solutes in the 10 wt \% water system (b). The
+  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
+  \end{subfigure}
+  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
+  smaller than those of the solutes in the 10 wt\% water system (b). The
   MSDs are not a monotonic function of molecular size (c and d). A significant
@@
   behavior. Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus
-  time of 3 representative ethanol centers of mass in the 10 wt \% water system.
+  time of 3 representative ethanol centers of mass in the 10 wt\% water system.
   There are clear periods of entrapment separated by relatively large hops.
@@
   dependent transport mechanisms. In general, we observed that hops 
-  made in the pore region are about 45 \% larger than those made outside
+  made in the pore region are about 45\% larger than those made outside
   the pore region (See Figure~\ref{fig:hop_lengths}). There is a high 
@@
   \end{subfigure}
-  \caption{(a) Hops made in the pore region of the 10 wt \% water system 
-  are, on average, 45 \% larger than those made outside the pore region. 
+  \caption{(a) Hops made in the pore region of the 10 wt\% water system 
+  are, on average, 45\% larger than those made outside the pore region. 
   The trend in hop lengths is similar to the trend in MSDs shown in 
@@
   bonding between hydrogen bond donor solutes and monomer head groups. To 
-  continue with our ethanol example, we observe that 64 \% of ethanol 
+  continue with our ethanol example, we observe that 64\% of ethanol 
   molecules donate hydrogen bonds  % 15.7/24 donated, 0.6/24 accept -- BJC: double check these numbers
-  and 3 \% of ethanol molecules accept hydrogen bonds each frame. On average, 40 \%
+  and 3\% of ethanol molecules accept hydrogen bonds each frame. On average, 40\%
   of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
-  head groups, 25 \% go to the ether linkages between the tails and the 
-  head groups and the remaining 35 \% to water. There are about 46 \% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molcules in pores 
+  head groups, 25\% go to the ether linkages between the tails and the 
+  head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molcules in pores 
   carboxylate oxygen atoms in the pore than there are water molecules yet more
@@
   average length of time that pairs stay coordinated. The degree and length of 
-  coordination between solutes and sodium in the 5 wt \% water system is higher
-  in all cases than that in the 10 wt \% water systems. The crowded pores of 
-  the 5 wt \% water system forces sodium ions in close proximity to solutes. 
+  coordination between solutes and sodium in the 5 wt\% water system is higher
+  in all cases than that in the 10 wt\% water systems. The crowded pores of 
+  the 5 wt\% water system forces sodium ions in close proximity to solutes. 
   The 5 highest coordinated solutes, which also have the longest coordinated dwell times,
@@
   the carbonyl and hydroxyl groups of carboxy-terminal groups in crystallized
-  ATPase.\cite{shinoda_crystal_2009}
-
-  Overall, the transport behavior exhibited by solutes in the 5 wt \% water
-  systems is similar to that shown by those in the 10 wt \% system however
+  ATPase.~\cite{shinoda_crystal_2009}
+
+  Overall, the transport behavior exhibited by solutes in the 5 wt\% water
+  systems is similar to that shown by those in the 10 wt\% system however
   the timescales are much longer. We observe subdiffusive behavior with 
@@
   of the same three trapping mechanisms. The frequency and 
-  length of hops are both diminished in the 5 wt \% system. Since there are
+  length of hops are both diminished in the 5 wt\% system. Since there are
   only 24 solute molecules in each system, in order to obtain better 
   time-averaged descriptions of solute transport mechanisms, we will focus
-  the remainder of our analysis on transport in the 10 wt \% water systems.
+  the remainder of our analysis on transport in the 10 wt\% water systems.
 
@@
   Figure~\ref{fig:multi_hbonds}). It has been observed that hydrogen bonding 
-  in a system will generally reduce diffusivity.\cite{srinivas_computer_1999}
+  in a system will generally reduce diffusivity.~\cite{srinivas_computer_1999}
 
@@
   infrequently, but regularly coordinate with sodium ions (see 
-  Figure~\ref{fig:ketones}). In an average frame, over 50 \% of acetic acid molecules
+  Figure~\ref{fig:ketones}). In an average frame, over 50\% of acetic acid molecules
   participate in hydrogen bonds with monomer head groups while less than 
-  10 \% of urea and acetamide molecules hydrogen bond with head groups. 
+  10\% of urea and acetamide molecules hydrogen bond with head groups. 
   Urea and acetamide both have hydrogen bond donating nitrogen atoms, however
   nitrogen is a weaker hydrogen bond donor than oxygen due to its lower 
-  electronegativity.\cite{biswal_hydrogen_2015} Given their lower propensity
+  electronegativity.~\cite{biswal_hydrogen_2015} Given their lower propensity
   to hydrogen bond, one might expect amides to partition out of the pore 
@@
   density of mercaptoethanol molecules outside the pore region, where 
-  transport is inherently slower. Mercaptoethanol spends 20 \% less 
+  transport is inherently slower. Mercaptoethanol spends 20\% less 
   time in the pore region than ethylene glycol. Conversely, 
-  mercaptoethanol hydrogen bonds with head groups about 40 \% less 
+  mercaptoethanol hydrogen bonds with head groups about 40\% less 
   frequently, which is less than expected if equal amounts of both 
@@
 % (12.857 + 6.8215 + 0.803) / (20.2 + 11.969 + 1.935) = 0.6
-%  There are nearly 40 \% more mercaptoethanol 
+%  There are nearly 40\% more mercaptoethanol 
 %  molecules than ethylene glycol molecules beyond 0.8 nm  % ratios.py in figures folder
@@
   % (2.788 + 2.0975 + 0)/ (13.1 + 7.737 + 0.8965) = 0.22
-  Only 22 \% of the hydrogen bond interactions of 2,3-dimercapto-1-propanol
+  Only 22\% of the hydrogen bond interactions of 2,3-dimercapto-1-propanol
   involve sulfur. Because sulfur can only weakly hydrogen bond, 
@@
   DMSO has a comparable if not larger MSD than acetone even though it
-  is a slightly larger molecule. DMSO spends 17 \% more time in the pore
+  is a slightly larger molecule. DMSO spends 17\% more time in the pore
   than acetone. 
@@
 %  the peak exhibited by acetone near 0.2 nm, which is due to sodium ion association.
-  On average, 35 \% of DMSO molecules are coordinated to a sodium ion each
-  frame compared with 26 \% of acetone molecules. The pyramidal structure 
+  On average, 35\% of DMSO molecules are coordinated to a sodium ion each
+  frame compared with 26\% of acetone molecules. The pyramidal structure 
   of DMSO may force it to spend more time closer to the pore center which
@@
   Carbonyl groups continue to show high degrees of association with
-  sodium ions. Between 25 and 30 \% of propylene carbonate, dimethyl 
+  sodium ions. Between 25 and 30\% of propylene carbonate, dimethyl 
   formamide and ethyl acetate molecules are coordinated with sodium ions
@@
   dependent on LLC membrane water content. The MSD of these components is about
-  2 orders of magnitude larger in the 10 wt \% system than in the 5 wt \% system.
+  2 orders of magnitude larger in the 10 wt\% system than in the 5 wt\% system.
   As more water is added to the system, the pores become less crowded with monomer

### 2019-04-16 Ben_Manuscripts/transport/Draft.tex
New figures from new plotting scripts

@@
 \usepackage{amssymb}
+\usepackage{array}
 \usepackage{siunitx}
@@
 
-%MRS2: ``dependent -> selective?'' 
-\title{Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 \author{Benjamin J. Coscia}
@@
 
-%MRS2: I think it would be useful to have a picture of the pores to
+% MRS2: I think it would be useful to have a picture of the pores to 
 % allow people to visualize what was going on. ToC might be good, 
-% but I think that as people read, they need to see the 3D picture as well to think through things.
+% but I think that as people read, they need to see the 3D picture 
+% as well to think through things.
 
@@
   of an LLC membrane using atomistic molecular simulations. We 
-  %MRS2: 
-  find
-  %found
-  %MRS2: ``transport rate -> transport''
-  that the transport rate of a species is dependent not only on 
+  find that the transport of a species is dependent not only on 
   molecular size, but on chemical functionality as well. The 
@@
   hydraulic fracturing flowback water waste streams which would help mitigate
-  the effects of deep well injection and generate value.~\cite{dischinger_application_2017} 
-  %BJC: could make last point more general
-  %MRS2: ``generate value'' is pretty vague, yeah.
-
-%  All of these separations are possible with current commercial membrane
-%  separation techniques but they are too energy intensive to be worth the 
-%  capital investment needed to start the processes  
-% MRS2: maybe ``are possible'' -> ``are possible in part''?  Otherwise, it logically follows that they shouldn't have major drawbacks.
-  All of these separations are possible with current commercial membrane
+  the effects of deep well injection and can be sold for profit.~\cite{dischinger_application_2017}
+
+  All of these separations are possible in part with current commercial membrane
   separation techniques but suffer from serious drawbacks. Currently, reverse 
@@
   important to take advantage of material properties other than pore size. 
-  %MRS2: is ``complexity'' the right word? Can we be more specific?
-  Unfortunately, the complexity of LLC membranes has obscured the interpretation
-  of experimental transport studies.~\cite{dischinger_effect_2017}  % BJC: ref to Sarah?
-
-  %MRS2: odd to have a one sentence paragraph?  MAyber just join with the next paragraph.
+  Unfortunately, interactions between solutes and pore moieties have yielded
+  unclear trends in experimental transport studies.~\cite{dischinger_effect_2017}
+
   Molecular dynamics (MD) simulations can give us mechanistic insights with 
@@
   within LLC membrane nanopores and intelligently design new membranes for 
-  solute-specific separations.
-
-  In our previous work, we used MD simulations to determine the most likely 
-  structure of the hexagonal phase formed by the monomer Na-GA3C11, expanding 
-  upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
+  solute-specific separations. In our previous work, we used MD simulations to 
+  determine the most likely structure of the hexagonal phase formed by the monomer
+  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
   We developed techniques for equilibrating the hexagonal phase formed by neat 
@@
   we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
-%  Many of the separations we are interested in involve polar organic 
-%  compounds.
-
-  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
-  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
-  % them much thought. Just used their residue names
-  \begin{table}
-  \centering
-  \begin{tcolorbox}[%
-  	colframe=blue,
-  	title=\centering \textbf{Solute Names and Their Abbreviations},
-  	width=0.7\textwidth,
-  	box align=center,
-  	halign=center,
-  	valign=center,
-  	fontupper=\linespread{1}\selectfont]
-
-  \begin{multicols}{2}
-
-  \textbf{Name} \\
-  Acetic Acid \\
-  Acetamide \\
-  Acetone \\
-  Butanol \\
-  Dimethyl Formamide \\
-  2,3-Dimercapto-1-propanol \\
-  Dimethyl Sulfoxide \\
-  Ethyl Acetate \\ 
-  Ethanol \\
-  Ethylene Glycol \\
-  Glycerol \\
-  Methanol \\ 
-  Propylene Carbonate \\
-  Propylene Glycol \\
-  Propanol \\
-  Ribose \\
-  Mercaptoethanol \\
-  Tetrose \\
-  Tetrahydrofuran \\
-  Urea \\
-  \columnbreak
-
-  \textbf{Abbrevation} \\
-  ACH \\  
-  ACN \\
-  ATO \\
-  BUT \\
-  DMF \\
-  DMP \\
-  DMSO \\
-  EAC \\ 
-  ETH \\
-  GCL \\
-  GLY \\
-  MET \\
-  PCB \\ 
-  PG \\
-  PR \\
-  RIB \\ 
-  SOH \\ 
-  TET \\
-  THF \\ 
-  URE \\
-
-  \end{multicols}
-
-  %MRS2: can you put molecules in the table as well?
+  Note that, in order to avoid studying charge species, we have only studied
+  %BJC: citations for pKa's
+  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
+  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
+  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
+  same time as protonated acetic acid.
+
+%  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
+%  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
+%  % them much thought. Just used their residue names
+%  \begin{table}
+%  \centering
+%  \begin{tcolorbox}[%
+%  	colframe=blue,
+%  	title=\centering \textbf{Solute Names and Their Abbreviations},
+%  	width=0.7\textwidth,
+%  	box align=center,
+%  	halign=center,
+%  	valign=center,
+%  	fontupper=\linespread{1}\selectfont]
+%
+%  \begin{multicols}{2}
+%
+%  \textbf{Name} \\
+%  Acetic Acid \\
+%  Acetamide \\
+%  Acetone \\
+%  Butanol \\
+%  Dimethyl Formamide \\
+%  2,3-Dimercapto-1-propanol \\
+%  Dimethyl Sulfoxide \\
+%  Ethyl Acetate \\ 
+%  Ethanol \\
+%  Ethylene Glycol \\
+%  Glycerol \\
+%  Methanol \\ 
+%  Propylene Carbonate \\
+%  Propylene Glycol \\
+%  Propanol \\
+%  Ribose \\
+%  Mercaptoethanol \\
+%  Tetrose \\
+%  Tetrahydrofuran \\
+%  Urea \\
+%  \columnbreak
+%
+%  \textbf{Abbrevation} \\
+%  AcOH \\  % Acetic acid
+%  AcN \\  % Acetamide
+%  ACE \\  % Acetone
+%  BtOH \\  % Butanol
+%  DMF \\  % Dimethyl Formamide
+%  DMP \\  % 2,3-Dimercapto-1-propanol
+%  DMSO \\  % Dimethyl sulfoxide
+%  ETAC \\  % Ethyl Acetate
+%  EtOH \\  % ethanol
+%  EG \\  % ethylene glycol
+%  GLY \\  % glycerol
+%  MeOH \\  % methanol
+%  PC \\ % propylene carbonate
+%  PG \\  % propylene glycol
+%  PrOH \\  % propanol
+%  RIB \\ 
+%  ME \\ % mercaptoethanol
+%  TET \\
+%  THF \\ 
+%  URE \\
+%  
+%  \end{multicols}
+%  
+%  %MRS2: can you put molecules in the table as well?
 I think it would be better for reference.
@@
 You can potentially partially stagger them horizontally so the size can be OK?
-  \end{tcolorbox}
+%  \end{tcolorbox}
+%  \caption{}\label{table:abbreviations}
+%  \end{table}
+
+  \begin{table}[h!]
+  \centering
+%  \begin{minipage}{.4\textwidth}
+%  \tiny
+  \begin{tabular}{ |lcclcc| }
+    \hline
+    Name & Abbreviation & Structure & Name & Abbreviation & Structure \\ \hline
+
+	\color{blue}{Methanol} & \color{blue}{MeOH} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+   	\color{blue}{Ethanol} & \color{blue}{EtOH} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+  	\color{blue}{Propanol} & \color{blue}{PrOH} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{blue}{Butanol} & \color{blue}{BtOH} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{red}{Ethylene Glycol} & \color{red}{EG} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{red}{Propylene Glycol} & \color{red}{PG} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{red}{Glycerol} & \color{red}{GLY} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{red}{Tetrose} & \color{red}{TET} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{red}{Ribose} & \color{red}{RIB} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{green!40!olive}{Acetic Acid} & \color{green!40!olive}{AcOH} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+%    \hline
+%    \end{tabular}
+%    \end{minipage}%
+%    
+%    \begin{minipage}{.2\linewidth}
+%    \tiny
+%    \begin{tabular}{ | l c c | }
+%    \hline
+%    Name & Abbreviation & Structure \\ \hline
+    \color{green!40!olive}{Urea} & \color{green!40!olive}{URE} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{green!40!olive}{Acetamide} & \color{green!40!olive}{AcN} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{green!40!olive}{Acetone} & \color{green!40!olive}{ACE} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{orange}{Mercaptoethanol} & \color{orange}{ME} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{orange}{Dimethyl Sulfoxide} & \color{orange}{DMSO} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{orange}{2,3-Dimercapto-1-propanol} & \color{orange}{DMP} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{yellow!70!orange}{Tetrahydrofuran} & \color{yellow!70!orange}{THF} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{yellow!70!orange}{Dimethylformamide} & \color{yellow!70!orange}{DMF} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{yellow!70!orange}{Propylene Carbonate} & \color{yellow!70!orange}{PC} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+
+    \color{yellow!70!orange}{Ethyl Acetate} & \color{yellow!70!orange}{EAC} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \end{minipage} \\
+    \hline
+  \end{tabular}
+%  \end{minipage}
   \caption{}\label{table:abbreviations}
@@
   %MRS2: descriptions of experiements can be in the past.
-  %First, we will comment on the membrane's structure. 
+
   We first address the structure of the pores formed in the membrane.
-  Previously, we have
-  studied dry membrane systems and some systems with low water content. 
-  We will observe how the radial density of monomer components and water 
-  change within the oore based on membrane water content.
-
-  % BJC: I don't really explicity comment on the partitioning of solutes
-  % out of the pore. Maybe I can add some sort of chart. Need to think more.
-  % MRS2: it should be mentioned somewhere, probably worth a paragraph or so.  
-  % If WATER is much slower outside of the pores, everything else will be slow as well, so we can
-  % justify transport there not being interesting
-  %Then we will present 
-  We then present
-  our efforts to understand how small molecules, 
+  Previously, we have studied dry membrane systems and some systems with 
+  low water content. We will observe how the radial density of monomer 
+  components and water change within the pore based on membrane water content.
+
+  We then present our efforts to understand how small molecules, 
   including water, partition within the pores. From a macroscopic perspective,
@@
   necessarily stay confined to the centers of the pores or even within the 
-  pore region. 
-  %MRS2:
-  %We will 
-  We then study the gradient in composition of solutes and 
+  pore region. We then study the gradient in composition of solutes and 
   water and any resultant influence it might have on mechanistic properties.
-  %MRS2: tweak
-  %Finally, and for the bulk of this work, we will 
-  For the remainder of the paper, we 
-  present our observations 
+
+  For the remainder of the paper, we present our observations 
   and explanations of the observed transport mechanisms exhibited by water
@@
 
-  %MRS2: next line is a statement about what we want to do, not what we did?
-  %We want to understand
-  We investigate
-  the differences in solute motion, specifically its mean squared displacement 
-  (MSD), based on a solute's size, shape and chemical functionality. We will 
-  study the interactions between solutes, the membrane, and water in order to
-  determine which mechanism or mechanisms dominate.
+  We investigate the differences in solute motion, specifically its mean 
+  squared displacement (MSD), based on a solute's size, shape and chemical
+  functionality. We will study the interactions between solutes, the membrane,
+  and water in order to determine which mechanism or mechanisms dominate.
 
@@
 
+  In the 10 wt\% water system, water molecules that spend the majority of 
+  their time in the distal tail region move significantly slower than those
+  confined to the pore region. In Figure~\ref{fig:water_msd_comparison}, we 
+  constructed the MSD curves based on water molecules that spent > 95\% of their
+  time in the pore region. If we instead restrict our calculation to water molecules
+  that spend > 95\% of their time in the distal tail region, the MSD of distal tail
+  water decreases 8-fold compared to pore water.
+
+  % Changing pore radius does not change conclusion here.
+  In the 5 wt\% water system, water molecules that spend the majority of their 
+  time in the distal tail region have MSDs comparable to those of water molecules
+  which stay in the pore region. The MSD of distal tail water molecules is 1.71 nm$^2$,
+  which is actually higher than that of pore water. This anomaly is likely a consequence
+  of low density in the distal tails as well as structuring of water molecules. 
+  Water molecules are less likely to interact via hydrogen bonding while in the distal 
+  tail region since they are interspersed between chains, while they are in close
+  proximity in the pores.
+  % BJC: quantify this. Number of hbonds per frame.
+
   \subsubsection{Transport of Small Polar Solutes}\label{section:general_transport_solutes}
@@
 
+  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
+  % me maybe half a day to implement and generate results. Not sure if necessary though since
+  % I'm just going to say that I don't know what distribution it is and we are going to
+  % use a percentile.
+  Hydrogen bond lifetimes appear to be distributed according to a power law or an
+  exponential function. A number of researchers provide evidence that supports a 
+  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
+  studies were done on extremely short timescales relative to ours, outputting positions
+  every timestep. Voloshin et al. studied hydrogen bonding on multiple timescales and 
+  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
+  We do not collect data frequently enough to provide a sufficient answer to this 
+  question so we instead report the 95\textsuperscript{th} percentile of hydrogen bond dwell times.
+  This places emphasis on solutes with long dwell times.
+
   The lifetime of hydrogen bonds between solutes and monomer head groups tends to 

### 2019-04-16 Ben_Manuscripts/transport/figures/all_coord.py

@@ -1,0 +1,86 @@
+#!/usr/bin/env python
+
+from LLC_Membranes.analysis.coordination_number import System
+from LLC_Membranes.llclib import file_rw
+import numpy as np
+import matplotlib.pyplot as plt
+import names
+
+# run: coordination_number.py -t PR_nojump.xtc -g berendsen.gro -r NA -rc res -at O / O3 O4
+
+head_groups = True
+path = '/home/bcoscia/Documents/Gromacs/Transport/NaGA3C11'
+pickle = 'solute_NA_coordination.pl'
+savename = 'all_solutes_NA_coordination.pdf'
+
+residues = ['ACH', 'ACN', 'ATO', 'BUT', 'DMF', 'DMP', 'DMS', 'EAC', 'ETH', 'GCL', 'GLY', 'MET', 'PCB', 'PG', 'PR', 'RIB', 'SOH', 'TET', 'THF', 'URE']
+
+labels = np.array([names.abbreviation[r] for r in res])
+colors = np.array([names.color_dict[r] for r in res])
+
+try:
+        loaded = np.load('na_coord.npz')
+        n_5wt = loaded['n_5wt']
+        n_10wt = loaded['n_10wt']
+
+except FileNotFoundError:
+
+        n_5wt = np.zeros([len(residues), 2])
+        n_10wt = np.zeros([len(residues), 2])
+
+	for wt in [5, 10]:
+		for i, r in enumerate(residues):
+			loc = '%s/%s/%swt' % (path, r, wt)
+			print(loc)
+			sys = file_rw.load_object('%s/NA_O_coordination.pl')
+			n = [len(np.nonzero(sys.distances[t][i, :])[1]) for t in range(sys.t.n_frames)]
+			plt.plot(n)
+			plt.show()
+			print(n)
+			exit()
+			
+			
+
+#                         ACH    ACN     ATO    BUT     DMF     DMP    DMS    EAC    ETH    GCL      GLY     MET      PCB    PG        PR       RIB        SOH      TET       THF        URE
+#values_10wt = np.array([0.2900, 0.477, 0.264, 0.0915, 0.2904, 0.0694, 0.350, 0.2700, 0.122, 0.1615, 0.1546, 0.09302, 0.3000, 0.1697, 0.124979, 0.131129, 0.104375, 0.13825, 0.1469375, 0.60833]) * 100
+
[…]

### 2019-04-16 Ben_Manuscripts/transport/figures/hop_freq.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+from LLC_Membranes.analysis import hop_location
+import names
+
+residues = ['ACH', 'ACN', 'ATO', 'BUT', 'DMF', 'DMP', 'DMS', 'EAC', 'ETH', 'GCL', 'GLY', 'MET', 'PCB', 'PG', 'PR', 'RIB', 'SOH', 'TET', 'THF', 'URE']
+
+ci = .95
+path = "/home/bcoscia/Documents/Gromacs/Transport/NaGA3C11"
+wt = 10
+
+hopfreq = np.zeros([len(residues), 2])
+
+try:
+	loaded = np.load('hopfreq_ci_%.2f.npz' % ci)
+	hopfreq = loaded['hopfreq']
+
+except FileNotFoundError:
+	for i, r in enumerate(residues):
+		print(r)
+		full_path = '%s/%s/%swt' % (path, r, wt)
+		hops = hop_location.HopLocation('%s/PR_nojump.xtc' % full_path, '%s/berendsen.gro' % full_path, r)
+		hops.calculate_solute_partition(r=1.5, spline=True, membrane_residue='HII', write_tcl=False)
+		hops.hops_and_dwells(penalty=0.25, nframes_dwell=10, locations=True)
+		hopfreq[i] = hops.hop_frequency()
+
+	np.savez_compressed('hopfreq_ci_%.2f' % ci, hopfreq=hopfreq)
+
+ordered = np.argsort(hopfreq[:, 0])[::-1]
+labels = np.array([names.abbreviation[r] for r in residues])[ordered]
+colors = np.array([names.color_dict[r] for r in residues])[ordered]
+
+bar_width = 0.8
+opacity = 0.8
+index = np.arange(len(residues))
+fig, ax = plt.subplots()
+ax.tick_params(labelsize=14)
+ax.set_xticks(index)
+ax.set_xticklabels(labels, fontsize=14)
+[x.set_color(colors[i]) for i, x in enumerate(plt.gca().get_xticklabels())]
+plt.xticks(rotation=90)
+ax.bar(index, hopfreq[ordered, 0], bar_width, alpha=opacity, yerr=hopfreq[ordered, 1])
+ax.set_ylabel('Hop Frequency (ns$^{-1}$)', fontsize=14)
+savename = 'hopfreq_total.pdf'
+plt.tight_layout()
+plt.savefig(savename)
+plt.show()
+

### 2019-04-17 Ben_Manuscripts/transport/Draft.tex
Edits to draft

@@
   hop lengths are reported as their displacement the $z$-direction.
+  We reported the standard error in the average hop lengths by 
+  bootstrapping the hop lengths.
   % BJC: could add more detail about which algorithm and cost function
@@
 
-  \subsection{Identification of Hydrogen Bonds}\label{method:hbonds}
+  % This might change
+  We determined the frequency of hops by dividing the total number of 
+  hops by the total length of the simulation. We used the normal 
+  approximation in order to estimate the 95 \% confidence interval
+  of these estimates:
+  \begin{equation}
+  95\%~CI = 1.96 \sqrt{\dfrac{\lambda}{n}}
+  \end{equation}
+  where $\lambda$ is the average frequency of hops and n is the total
+  observation time accumulated for all solutes.
+
+  Where instructive, we differentiated between the length of hops inside
+  and outside of the pores. For 10 wt\% water systems, we consider a solute
+  to be in the pore if it is within 0.75 nm of a pore center. This radial
+  cut-off maximizes the difference between average hop lengths in and out
+  of the pore. See Section~\ref{S-section:pore-region} of the Supporting
+  Information for further details on this optimization.
+
+  \subsection{Time Spent in Pore Region}
+
+  Using the cut-off defined above, we calculated the fraction of time
+  that a solute spends within the pore region. Since this is a process
+  with two possible outcomes, we calculated the standard error ($SE$) of our
+  calculations based on the binomial theorem: 
+  \begin{equation}
+  SE = \sqrt{\dfrac{p(1-p)}{n}}
+  \end{equation}
+  where $p$ is the probability that a solute is in the pore region and
+  $n$ is the sample size. Here $n$ is the total number of transitions
+  between each region.
+
+  \subsection{Identification and Analysis of Hydrogen Bonds}\label{method:hbonds}  % Could just make title 'Hydrogen Bonds'
 
@@
 
+  We determined the average percentage of solutes which actively participated
+  in a hydrogen bond interaction with monomers each frame. We only counted
+  unique solute--monomer hydrogen bond interactions meaning solutes
+  that hydrogen bond more than once simultaneously were classified as a
+  single pairing event. We determined the standard error of this calculation
+  by bootstrapping over each solute's trajectory. For each bootstrap trial,
+  we randomly chose 24 solutes with replacement and calculated the average
+  active solute-monomer hydrogen bonds per frame.
+
   \subsection{Coordination Number}\label{method:coordination}
@@
 
+  We determined the average percentage of solutes actively coordinated to
+  a sodium ion each frame. Our calculation procedure is analogous to that for
+  solute-monomer hydrogen bond interactions outlined in the previous section.
+
   \subsection{Association Lifetimes}\label{method:lifetimes}
@@
 
-  We found that the distributions best fit a power law / exponential
-  distribution.
-  % BJC: need to do this. 
-  % BJC: reporting median doesn't work great since it is usually equal
-  % to the lowest possible value since time step is large.
-  % Would probably be better to report fit parameters (alpha for power law)
-  % Could use those values in analytical equations for median
+  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
+  % me maybe half a day to implement and generate results. Not sure if necessary though since
+  % I'm just going to say that I don't know what distribution it is and we are going to
+  % use a percentile.
+  Hydrogen bond lifetimes appear to be distributed according to a power law or an
+  exponential function. A number of researchers provide evidence that supports a 
+  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
+  studies were done on extremely short timescales relative to ours, outputting positions
+  every time step. Voloshin et al. studied hydrogen bonding on multiple timescales and 
+  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
+  Due to memory limitations, we could not collect data frequently enough to provide a
+  sufficient answer to this question so we instead report the 95\textsuperscript{th} 
+  percentile of hydrogen bond dwell times. This places emphasis on solutes with 
+  long dwell times. We reported the standard error of this calculation by bootstrapping
+  the distribution of dwell times.
+
+  The distribution of sodium association lifetimes appear similar to
+  hydrogen bond life time distributions. Therefore, we reported association
+  lifetimes in the same manner as hydrogen bond lifetimes.
 
@@
 
-  Before beginning the analysis of transport behavior, it is important to
+  Before beginning the analysis of solute transport behavior, it is important to
   elucidate the topology of the membrane pores in solvated systems.
 
-  In contrast to our previous work with a dry version of this 
-  membrane, the pore region of the 5 and 10 wt\% water 
-  systems are primarily filled with water and sodium ions. We define the
-  pore region based on the average COM position of the monomer head groups' 
-  % BJC: not sure the best place in paper to define pore region. Maybe a system definitions section in Methods.
-  % BJC: need to decide on exact definition. Should probably be the same as the 'Head Groups' line
-  carboxylate oxygen atoms. Figure~\ref{fig:component_densities} plots the RDF of each membrane
-  constituent in the dry system as well as the 5 and 10 wt\% water systems. 
-  In dry systems, the pore center is densely filled with sodium ions and head
-  groups. The peak head group density occurs within 0.25 nm of the pore center.
-  In hydrated systems, water occupies, and is densest, at the center of each 
-  pore. The density of sodium ions is somewhat uniform in the pore center of
-  the 5 wt\% water system while it shows a maximum closer to the head groups
-  in the 10 wt\% water system. The peak density of sodium ions is not at the
-  pore center in the 10 wt\% water system likely because they are still
-  loosely associated with the monomer's carboxylate head groups.
+  In contrast to our previous work with a dry version of this membrane, the 
+  region close to the pore center of the 5 and 10 wt\% water systems is 
+  primarily filled with water and sodium ions. Figure~\ref{fig:component_densities}
+  plots the RDF of each membrane constituent in the dry system as well as the
+  5 and 10 wt\% water systems. In dry systems, the pore center is densely 
+  filled with sodium ions and head groups. The peak head group density occurs
+  within 0.25 nm of the pore center. In hydrated systems, water occupies, 
+  and is densest, at the center of each pore. The density of sodium ions is 
+  somewhat uniform in the pore center of the 5 wt\% water system while it shows
+  a maximum closer to the head groups in the 10 wt\% water system. The peak 
+  density of sodium ions is not at the pore center in the 10 wt\% water system
+  likely because they are still loosely associated with the monomer's carboxylate
+  head groups.
 
@@
   systems is about 0.2 nm further from the pore center than the 5 wt\% water system. 
-  Based on these observations, we expect solute transport to be fastest in the 10 wt
- \% water system.
+  Based on these observations, we expect solute transport to be fastest in the 
+  10 wt\% water system.
 
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{component_density_dry.pdf}
+  \includegraphics[width=\textwidth]{component_density_dry.pdf}  % running this out on bridges to make smoother
   %BJC: simulation is extended to smooth out these curves
@@
   \caption{The radial densities of various monomer components paint a 
-  picture of the pore topology where the pore centers are primarily composed
+  picture of the pore topology where the pore centers of hydrated systems are primarily composed
   of water and sodium ions. The monomer groups labeled in each plot correspond to 
@@
 
-  There is an appreciable amount of water that partitions into the distal tail
-  region of both systems. 28\% and 31\% of the total water is present in the tail
-  regions of the 5 and 10 wt\% water systems respectively. See 
-  Section~\ref{S-section:water_content_equil} of the Supporting Information for more details. This 
-  result is due to a combination of the lower density of the tail region
-  as well as oxygen atoms at the ends of each monomer tail which can further 
-  stabilize water molecules. See Figure~\ref{S-fig:total_density} of the 
-  Supporting Information for a graphical illustration of this point.
+  There is an appreciable amount of water that partitions into the distal tail % BJC: defined in methods
+  region of both systems. 28\% and 31\% of the total water is present in the
+  tail regions of the 5 and 10 wt\% water systems respectively. See 
+  Section~\ref{S-section:water_content_equil} of the Supporting Information 
+  for more details on the equilibration that led to this conclusion. The partition
+  is due to a combination of the distal tail region's lower density as well
+  as oxygen atoms at the ends of each monomer tail which can further stabilize
+  water molecules. See Figure~\ref{S-fig:total_density} of the Supporting 
+  Information for a graphical illustration of this point.
 
@@
   solutes. Then we will present the general trends that we observe among the
-  set of solutes studied.
+  all other solutes studied.
 
@@
   their time in the distal tail region move significantly slower than those
-  confined to the pore region. In Figure~\ref{fig:water_msd_comparison}, we 
-  constructed the MSD curves based on water molecules that spent > 95\% of their
-  time in the pore region. If we instead restrict our calculation to water molecules
-  that spend > 95\% of their time in the distal tail region, the MSD of distal tail
-  water decreases 8-fold compared to pore water.
+  close to the pore center. In Figure~\ref{fig:water_msd_comparison}, we 
+  constructed the MSD curves based on water molecules that spent $>$ 95\% of their
+  time outside the distal tail region. If we instead restrict our calculation to
+  water molecules that spend $>$ 95\% of their time in the distal tail region, 
+  the MSD of distal tail water decreases 8-fold.
 
@@
   time in the distal tail region have MSDs comparable to those of water molecules
-  which stay in the pore region. The MSD of distal tail water molecules is 1.71 nm$^2$,
-  which is actually higher than that of pore water. This anomaly is likely a consequence
-  of low density in the distal tails as well as structuring of water molecules. 
-  Water molecules are less likely to interact via hydrogen bonding while in the distal 
-  tail region since they are interspersed between chains, while they are in close
-  proximity in the pores.
-  % BJC: quantify this. Number of hbonds per frame.
+  close to the pore center. The MSD of distal tail water molecules is 1.71 nm$^2$.
+  This anomaly is likely a consequence of low density in the distal tails (see
+  Figure~\ref{S-fig:total_density}) as well as structuring of water molecules via
+  hydrogen bonding. Water molecules are less likely to hydrogen bond while in the
+  distal tail region since they are interspersed between chains, while those in 
+  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
+  hydrogen bonding between water molecules near the pore center versus those in 
+  the distal tail region. While a similar observation holds for the 10 wt\% system,
+  its high water content facilitates a less crowded environment where diffusion
+  of water molecules dominates.
 
@@
   subsets of similar molecules.
-%  where some exceptions occur.
-
-%  We have gained a clearer picture of the general transport properties exhibited by
-%  this system through the collective study of all solutes. We will first address the
-%  questions posed in the introduction in a general sense before addressing them with
-%  respect to specific molecules, where exceptions occur.
-%  \bigskip
 
@@
   system (Figure~\ref{fig:msds}). The fastest moving solute in both cases, 
-  methanol, has an MSD about 175 times larger in the 10 wt\% versus the 5 wt 
- \% water system. Clearly the equilibrium water content of a given LLC system will 
-  determine its viability for real separations.
+  methanol, has an MSD about 175 times larger in the 10 versus the 5 wt\%
+  water system. Clearly the equilibrium water content of a given LLC system will 
+  determine its viability for real separations.  % BJC: last sentence too much speculation?
 
@@
   so that it intersected methanol's MSD. The uncorrected version of 
-  Equation~\ref{eqn:stokes-einstein} is plotted and converges to the same value as the
+  Equation~\ref{eqn:stokes-einstein} ($f$=1) is plotted and converges to the same value as the
   corrected form for large radii (see Section~\ref{method:stokes}). Although both curves are 
@@
   In general, the longest dwell times occur when solutes are situated far from the
-  pore center and the hops occur when solutes are close to the pore center. (b) The
-  time-averaged MSD of ethanol is sub-linear which suggests transport is governed 
-  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
+  pore center and more frequent hops occur when solutes are close to the pore center.
+  (b) The time-averaged MSD of ethanol is sub-linear which suggests transport is
+  governed by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
   \end{figure}
@@
   dependent transport mechanisms. In general, we observed that hops 
-  made in the pore region are about 45\% larger than those made outside
-  the pore region (See Figure~\ref{fig:hop_lengths}). There is a high 
+  made in the pore region are about 59\% larger than those made outside
+  the pore region (see Figure~\ref{fig:hop_lengths}). There is a high 
   resistance to movement in the alkane-dense head group and tail regions
@@
   frequency (see Figure~\ref{fig:hopfreq}). Therefore, trapping mechanisms
-  controlled by membrane properties other than density must be prevalent.
+  controlled by membrane properties other than alkane density must be prevalent.
 
@@
   \caption{(a) Hops made in the pore region of the 10 wt\% water system 
-  are, on average, 45\% larger than those made outside the pore region. 
+  are, on average, 59\% larger than those made outside the pore region. 
   The trend in hop lengths is similar to the trend in MSDs shown in 
@@
   example, ribose spends the largest fraction of time in the pore region, yet
-  performs the the second lowest number of hops.}\label{fig:hops}
+  hops the fifth least frequently.}\label{fig:hops}
   \end{figure}
 
-  In addition to solute trapping in dense monomer regions, 
-  we observe a second trapping mechanism caused by preferential hydrogen 
+  %In addition to solute trapping in dense monomer regions, 
+  We observe a second trapping mechanism caused by preferential hydrogen 
   bonding between hydrogen bond donor solutes and monomer head groups. To 
@@
   of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
-  head groups, 25\% go to the ether linkages between the tails and the 
+  head groups, 25\% go to the ether linkages connecting the monomers tails to the 
   head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molcules in pores 
@@
 
-  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
-  % me maybe half a day to implement and generate results. Not sure if necessary though since
-  % I'm just going to say that I don't know what distribution it is and we are going to
-  % use a percentile.
-  Hydrogen bond lifetimes appear to be distributed according to a power law or an
-  exponential function. A number of researchers provide evidence that supports a 
-  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
-  studies were done on extremely short timescales relative to ours, outputting positions
-  every timestep. Voloshin et al. studied hydrogen bonding on multiple timescales and 
-  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
-  We do not collect data frequently enough to provide a sufficient answer to this 
-  question so we instead report the 95\textsuperscript{th} percentile of hydrogen bond dwell times.
-  This places emphasis on solutes with long dwell times.
-
   The lifetime of hydrogen bonds between solutes and monomer head groups tends to 
@@
   we see nearly the same ordering of the percentage of solutes hydrogen bonded to
-  monomer head groups and the mean hydrogen bond lifetime. Solutes with multiple
-  hydroxyl groups donate hydrogen bonds most frequently and tend to stay hydrogen
-  bonded longer. Hydrogen bonds donated by nitrogen are far less common and tend 
-  to be short-lived as supported by acetamide and urea.
+  monomer head groups and the 95\textsuperscript{th} percentile of hydrogen bond 
+  lifetimes. Solutes with multiple hydroxyl groups donate hydrogen bonds most 
+  frequently and tend to stay hydrogen bonded longer. Hydrogen bonds donated by
+  nitrogen are far less common and tend to be short-lived as shown by acetamide
+  and urea.
 
@@
   of sodium ions coordinated to the oxygen atoms of each solute as well as the
-  average length of time that pairs stay coordinated. The degree and length of 
+  95\textsuperscript{th} percentile of sodium association times. The degree and length of 
   coordination between solutes and sodium in the 5 wt\% water system is higher
@@
   the 5 wt\% water system forces sodium ions in close proximity to solutes.
-  The 5 highest coordinated solutes, which also have the longest coordinated dwell times,
-  all contain carbonyl groups (except for dimethyl sulfoxide which has an 
-  analogous sulfinyl group) which leaves a highly electron-dense oxygen atom 
-  exposed and ready to interact with sodium. 
-  %BJC: need to verify following  
-  The dwell times are power law 
-  distributed, which means that while many of these interactions are fleeting,
-  there is still a chance for very long periods of association to occur. For 
-  example, the longest period of coordination between acetone and sodium was
-  110 ns.
+
+  Carbonyl functional groups tend to associate with sodium the most. Nearly
+  all of the most coordinated solutes contain a carbonyl group (except for 
+  DMSO which has an analogous sulfinyl group). There is a significant
+  drop in sodium ion association for solutes that do not contain carbonyl 
+  groups or multiple hydroxyl groups to compensate. The corresponding dwell
+  times follow a similar trend, however the dwell times of highly coordinated 
+  solutes with multiple hydroxyl groups are generally lower since association
+  between hydroxyl groups and sodium is apparently a weaker interaction. Carbonyl
+  groups contain an exposed and highly electron-dense oxygen atom which interacts
+  readily with sodium ions. Carbonyl groups with nitrogen substituents appear
+  to interact with sodium more frequently than those with carbon substituents. 
+  Acetone associates with sodium significantly less than urea and acetamide.
+
+%  The dwell times are power law 
+%  distributed, which means that while many of these interactions are fleeting,
+%  there is still a chance for very long periods of association to occur. For 
+%  example, the longest period of coordination between acetone and sodium was
+%  110 ns.
 %  There are many cases, particularly when an electronegative atom is left unprotected,
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{all_solutes_NA_coordination.pdf}
+  % BJC: maybe I should normalize these to number of oxygen atoms?
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{all_solutes_NA_coordination.pdf}  % all_coord.py
   \caption{}\label{fig:all_solutes_NA_coordination}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{all_NA_dwells.pdf}
+  \includegraphics[width=\textwidth]{all_NA_dwells.pdf}  % na_dwells.py
   \caption{}\label{fig:all_NA_dwells}
@@
   Carvajal et al. noted that Na\textsuperscript{+} coordinated with four 
-  tetrahydrofuran molecules when they dissolved a sodium salt in the solvent.~\cite{carvajal_studies_1965}
+  THF molecules when they dissolved a sodium salt in the solvent.~\cite{carvajal_studies_1965}
   Wu et al. observed coordination of Na\textsuperscript{+} with the carbonyl
@@
   time in the pore region than most other solutes. However, even outside the pore
-  region, hops made by methanol are larger than those by any other solute. The
-  small size of methanol allows it to move relatively unhindered.
+  region, hops made by methanol are larger than those made by almost any other solute
+  in the pore region. The small size of methanol allows it to move relatively unhindered.
 
@@
   hydrogen bonding with the carboxylate oxygen atoms for all simple alcohols. 
-  This is largely due to the large net charge of the carboxylate groups as well
+  This is largely due to the high net charge of the carboxylate groups as well
   as the more highly crowded environment surrounding the ether oxygen atoms. 
@@
   a given alcohol's preference towards hydrogen bonds with the carboxylate groups
-  of ether linkages increases with molecule size. (d) The average location of 
+  of ether linkages increases with increasing hydrophobic character. (d) The average location of 
   butanol's oxygen atom is closer to the pore center than its most distal carbon
@@
   four hydroxyl groups of Ribose (n = 4) are involved in a hydrogen bond interaction
-  at the same time.}\label{fig:multi_hbonds}
+  at the same time.}\label{fig:polyols}
   \end{figure}
@@
   ethylene glycol increases propylene glycol's hydrophobic character and causes
-  it to favor positions near monomer head groups. Both diols have comparable 
-  densities close to the pore center, however propylene glycol's density has a
-  large peak near the monomer head groups relative to ethylene glycol. Propylene
-  glycol can form more highly stabilized hydrogen bonds with carboxylate groups,
-  explaining the slightly higher incidence of hydrogen bonds shown in 
-  Figure~\ref{fig:multi_hbonds}. The average hydrogen bond lifetime of propylene
-  glycol with monomers is 1.95 ns compared to 1.34 ns for ethylene glycol.  % BJC: 2.33 ns vs 1.62 ns for hbonds with carboxylate
-  Somewhat counterintuitively, there is a relatively high density of ethylene
-  glycol molecules beyond the head group region probably due to its relatively 
-  small size. This likely contributes to the somewhat large error bars on its MSD
-  in Figure~\ref{fig:msds}.
+  it to favor positions near monomer head groups (see Figure~\ref{fig:polyols_rdf}).
+  Both diols have comparable densities close to the pore center, however propylene
+  glycol's density has a large peak near the monomer head groups relative to 
+  ethylene glycol. Propylene glycol can form more highly stabilized hydrogen 
+  bonds with carboxylate groups, explaining the slightly higher incidence of 
+  hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}. The 95\textsuperscript{th}
+  percentile of hydrogen bond lifetimes for propylene glycol with monomers is 9.51 ns
+  compared to 7 ns for ethylene glycol. 
+  %BJC: not sure of following point is worthwhile  
+  Somewhat counterintuitively, there is a 
+  relatively high density of ethylene glycol molecules beyond the head group region
+  probably due to its relatively small size. This likely contributes to the somewhat
+  large error bars on its MSD in Figure~\ref{fig:msds}.
 
@@
 
-  The 4 ketone-like molecules tested show a surprising range of transport
-  behaviors. Urea, acetic acid, acetamide and acetone are all characterized by
+  The 4 ketone-like molecules tested show a range of transport behaviors. 
+  Urea, acetic acid, acetamide and acetone are all characterized by
   a carbonyl group with two attached heavy atoms. All are similar in size and
@@
   \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}
+  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}  %BJC: need error bars!
   \caption{}\label{fig:ketone_hbonds}
@@
   \caption{(a) The MSD of the solutes decreases and the deviation from
-  Stokes-Einstein predicted behavior increases as with molecular size increases.
+  Stokes-Einstein predicted behavior increases with molecular size.
   (b) The radial density near the pore center (r = 0) decreases with decreasing
@@
   MSD. The range of behaviors shown by mercaptoethanol help explain the
-  large variance of its MSD. Some can be accounted for by the higher 
+  large variance of its MSD. Much can be accounted for by the higher 
   density of mercaptoethanol molecules outside the pore region, where 
-  transport is inherently slower. Mercaptoethanol spends 20\% less 
-  time in the pore region than ethylene glycol. Conversely, 
-  mercaptoethanol hydrogen bonds with head groups about 40\% less 
-  frequently, which is less than expected if equal amounts of both 
-  solutes occupied the pore region. Consequently, shorter hydrogen 
-  bond lifetimes within the pore region may yield some high MSD 
-  trajectories.
-
+  transport is inherently slower. Although both solutes
+  hop with a similar magnitude inside and outside of the pore region, mercaptoethanol 
+  spends about 18\% less time in the pore region (see Figure~\ref{fig:hops}).
+  This has a large impact on its hop frequency which is 42\% lower than that 
+  of ethylene glycol. This implies that mercaptoethanol is relatively
+  immobile outside of the pore, but moves quickly inside.
+%  Mercaptoethanol also hydrogen bonds with head groups about 16\% less 
+%  %BJC: 16\% less meaning 64.3 % - 48.3 %. Not sure if it is better to say (64.3 - 48.3 / 64.3) = 25 %
+%  frequently. Consequently, shorter hydrogen 
+%  bond lifetimes within the pore region may yield some high MSD 
+%  trajectories.
+
+%, which is less than expected if equal amounts of both 
+%  solutes occupied the pore region. 
 % (20.2 - 12.857) / 20.2 = .364
@@
   because more of it partitions into the tail region. 2,3-dimercapto-1-propanol
-  spends 38\% less time in the pore region than glycerol.
+  spends 27\% less time in the pore region than glycerol. 
+  %BJC: again, not sure if this should be 27\% because DMP spends 49% of time in pore and GLY spends 76% of time in pore or if it should be (76 - 49) / 76 = 36 %
 %  The density of glycerol is always higher up to 0.7 nm from the pore center where the 
@@
   Glycerol participates in about 2.5 times as many hydrogen
-  bonds as 2,3-dimercapto-1-propanol. % which is consistent with the number of hydroxyl groups per solute. 
+  bonds as 2,3-dimercapto-1-propanol (including all possible hydrogen bonding groups).  % BJC: might be confusing. Maybe refer to figure 6 instead.
   % BJC: sums are (donate to monomer + recieve from water + donate to water).
@@
 
-  DMSO has a comparable if not larger MSD than acetone even though it
-  is a slightly larger molecule. DMSO spends 17\% more time in the pore
-  than acetone. 
+  DMSO has a comparable MSD to acetone even though it is a larger molecule. 
+  DMSO spends 17\% more time in the pore than acetone. 
 %  The density of DMSO is higher than acetone in the pore region, except for
@@
   cannot donate them. Among this set are the two slowest solutes in our study: 
-  tetrahydrofuran and dimethyl formamide. The MSDs of ethyl acetate, propylene
-  carbonate and acetone are only marginally larger.
+  THF and DMF. The MSDs of ethyl acetate, propylene carbonate and acetone are
+  only marginally larger.
 
@@
   dimethyl formamide (Figure~\ref{fig:hop_lengths}). Acetone and 
-  tetrahydrofuran perform slightly larger hops but have the third and
-  first lowest hop frequencies respectively (see Figure~\ref{fig:hopfreq}).
+  tetrahydrofuran perform slightly larger hops but low hop frequencies
+  (see Figure~\ref{fig:hopfreq}).
 
@@
   However, this is not a hard rule. When a solute does overcome the 
-  barrier of entry beyond the head group region, it can become trapped. All
-  solutes in this set show at least a small peak $\geq$ 0.9 nm from the pore 
-  center which is likely caused by solutes that get trapped in the tail region
-  for significant periods of time.
+  barrier of entry beyond the pore region, it can become trapped. All
+  solutes in this set show at least a small peak in the pore region which
+  is likely caused by solutes that get trapped in the tail region for 
+  significant periods of time.
 
@@
   (see Figure~\ref{fig:ketone_hbonds}).
-  Assocaition between sodium and solutes in this set are also among the longest,
+  Association between sodium and solutes in this set are also among the longest,
   only beat by other solutes with carbonyl groups and ribose.

### 2019-04-17 Ben_Manuscripts/transport/Supporting_Information.tex
Edits to draft

@@
 
+  \section{Pore Region Definition}\label{section:pore-region}
+
+  We performed a sensitivity analysis in order to determine the radial 
+  cut-off that maximizes the difference in hop lengths in and out of 
+  the pore region. We varied the location of the cut-off defining the
+  edge of the pore region in increments of 0.05 from 0.3 to 0.7. We
+  varied the cut-off in increments of 0.1 from 0.7 to 0.8 in order to
+  increase our resolution about the maximum (see Figure~\ref{fig:pore_cutoff}). 
+  Defining the cut-off 0.75 nm from the pore center maximizes the 
+  difference in hop lengths between solutes in and out of the pore.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\linewidth]{pore_cutoff.pdf}
+  \caption{Defining the cut-off 0.75 nm from the pore center maximizes the 
+  difference in hop lengths between solutes in and out of the pore. We 
+  varied the location of the cut-off defining the edge of the pore region
+  in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
+  increments of 0.1 from 0.7 to 0.8 in order to increase our resolution
+  about the maximum.}\label{fig:pore_cutoff}
+  \end{figure}
+
   \section{Pore Splines}\label{section:splines}

### 2019-04-17 Ben_Manuscripts/transport/figures/na_dwells.py

@@ -87,10 +87,10 @@ ax.set_xticklabels(labels, fontsize=14)
 plt.xticks(rotation=90)
 
 plt.gcf().get_axes()[0].tick_params(labelsize=14)
-plt.ylabel('Mean Dwell Time (ns)', fontsize=14)
+plt.ylabel('95$^{th}$ Percentile Dwell Time (ns)', fontsize=14)
 plt.gca().set_ylim(bottom=0.5)
 plt.legend(fontsize=14)
 fig.tight_layout()
-#plt.savefig(savename)
+plt.savefig(savename)
 plt.show()
 

### 2019-04-18 Ben_Manuscripts/transport/Draft.tex
Formatted solute table

@@
 %  \tiny
-  \begin{tabular}{ |lcclcc| }
+%  \begin{tabular}{ |lcc|lcc| }
+  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
     \hline
-    Name & Abbreviation & Structure & Name & Abbreviation & Structure \\ \hline
-
+    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
+    \hline
 	\color{blue}{Methanol} & \color{blue}{MeOH} &     
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/MET.pdf}
+    \end{minipage} &
+
+    \color{green!40!olive}{Urea} & \color{green!40!olive}{URE} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/URE.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/ETH.pdf}
+    \end{minipage} &
+
+    \color{green!40!olive}{Acetamide} & \color{green!40!olive}{AcN} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/ACN.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/PR.pdf}
+    \end{minipage} &
+
+    \color{green!40!olive}{Acetone} & \color{green!40!olive}{ACE} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/ATO.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/BUT.pdf}
+    \end{minipage} &
+
+    \color{orange}{Mercaptoethanol} & \color{orange}{ME} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/SOH.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/GCL.pdf}
+    \end{minipage} &
+
+    \color{orange}{Dimethyl Sulfoxide} & \color{orange}{DMSO} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/DMS.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/PG.pdf}
+    \end{minipage} &
+
+    \color{orange}{2,3-Dimercapto-1-propanol} & \color{orange}{DMP} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/DMP.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/GLY.pdf}
+    \end{minipage} &
+
+    \color{yellow!70!orange}{Tetrahydrofuran} & \color{yellow!70!orange}{THF} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/THF.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/TET.pdf}
+    \end{minipage} &
+
+    \color{yellow!70!orange}{Dimethylformamide} & \color{yellow!70!orange}{DMF} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/DMF.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/RIB.pdf}
+    \end{minipage} &
+
+    \color{yellow!70!orange}{Propylene Carbonate} & \color{yellow!70!orange}{PC} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/PCB.pdf}
     \end{minipage} \\
@@
     \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
+    \includegraphics[width=\linewidth]{structures/ACH.pdf}
+    \end{minipage} &
+
+    \color{yellow!70!orange}{Ethyl Acetate} & \color{yellow!70!orange}{EAC} &     
+    \begin{minipage}{.1\textwidth}
+    \includegraphics[width=\linewidth]{structures/EAC.pdf}
     \end{minipage} \\
-%    \hline
-%    \end{tabular}
-%    \end{minipage}%
-%    
-%    \begin{minipage}{.2\linewidth}
-%    \tiny
-%    \begin{tabular}{ | l c c | }
-%    \hline
-%    Name & Abbreviation & Structure \\ \hline
-    \color{green!40!olive}{Urea} & \color{green!40!olive}{URE} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{green!40!olive}{Acetamide} & \color{green!40!olive}{AcN} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{green!40!olive}{Acetone} & \color{green!40!olive}{ACE} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{orange}{Mercaptoethanol} & \color{orange}{ME} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{orange}{Dimethyl Sulfoxide} & \color{orange}{DMSO} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{orange}{2,3-Dimercapto-1-propanol} & \color{orange}{DMP} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{yellow!70!orange}{Tetrahydrofuran} & \color{yellow!70!orange}{THF} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{yellow!70!orange}{Dimethylformamide} & \color{yellow!70!orange}{DMF} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{yellow!70!orange}{Propylene Carbonate} & \color{yellow!70!orange}{PC} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
-
-    \color{yellow!70!orange}{Ethyl Acetate} & \color{yellow!70!orange}{EAC} &     
-    \begin{minipage}{.1\textwidth}
-    \includegraphics[width=\linewidth]{structures/methanol.png}
-    \end{minipage} \\
+
     \hline
@@
 %  \end{minipage}
-  \caption{}\label{table:abbreviations}
+  \caption{Names of solutes along with their molecular structures and the
+  abbreviations which we use in this paper. Colors corresponds to solute groupings
+  and are used in many plots. Blue corresponds to simple alcohols, red to 
+  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
+  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.}\label{table:abbreviations}
+  % BJC: achemso for jpcb makes table captions bold
+  % BJC: also, it's published that way
   \end{table}

### 2019-04-18 Ben_Manuscripts/transport/Draft.tex
updated citations
minor changes

@@
 
-  % This might change
   We determined the frequency of hops by dividing the total number of 
-  hops by the total length of the simulation. We used the normal 
-  approximation in order to estimate the 95 \% confidence interval
-  of these estimates:
-  \begin{equation}
-  95\%~CI = 1.96 \sqrt{\dfrac{\lambda}{n}}
-  \end{equation}
-  where $\lambda$ is the average frequency of hops and n is the total
-  observation time accumulated for all solutes.
+  hops by the total length of the simulation. We used the average
+  frequency as the $\lambda$ parameter in a Poisson distribution. We
+  calculated the 95\% confidence intervals of the distribution based
+  on its cumulative distribution function.
+
+%  We used the normal 
+%  approximation in order to estimate the 95 \% confidence interval
+%  of these estimates:
+%  \begin{equation}
+%  95\%~CI = 1.96 \sqrt{\dfrac{\lambda}{n}}
+%  \end{equation}
+%  where $\lambda$ is the average frequency of hops and n is the total
+%  observation time accumulated for all solutes.
 
@@
   \begin{subfigure}{0.45\textwidth}
+  % BJC: update legends with abbreviations?
   \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
@@
   \begin{subfigure}{0.325\textwidth}
+  %BJC: trying out pore region cut-off here instead of head groups.
   \includegraphics[width=\textwidth]{nondonors_rdf.pdf}

### 2019-04-19 Ben_Manuscripts/comps/Outline.tex
UPdates to comps outline

@@
   % re-word. This paragraph is verbatim from structure paper
-  More highly selective nanoporous membranes would be extremely useful
-  in performing complex aqueous separations with seawater and various
+  More highly selective nanoporous membranes would be useful for 
+  performing complex aqueous separations with seawater and various
   types of wastewater.
   \begin{itemize}
-    \item For example, Sodium chloride and boron in seawater 
+    \item For example, sodium chloride and boron in seawater 
     \cite{fritzmann_state---art_2007} and organic micropollutants found in
@@
     required membrane passes and post-treatment steps needed for a given 
-    filtration process \cite{werber_materials_2016}, thus lowering energy
-    requirements. 
-    \item Additionally, one can also extract valuable resources from the 
+    filtration process \cite{werber_materials_2016}, thus lowering cost
+    and energy requirements. 
+    \item Additionally, one can extract valuable resources from the 
     feed streams. For example, flowback water produced during hydraulic
@@
     \item RO separates solutes based on the solute's ability to dissolve into
-    and diffuse through the tortuous pathways available in dense active layer.
+    and diffuse through the tortuous pathways available in the membrane's dense 
+    active layer.
     \item RO offers high selectivity at the cost of relatively high energy 
-    requirements since one must apply a large hydraulic pressure in order to 
-    achieve an economical flux.  % get number
+    requirements since one must apply hydraulic pressure of up to 100 bar in 
+    order to achieve an economical flux~\cite{van_der_bruggen_review_2003}.  % get number
     \item In contrast to RO membranes, NF membranes have explicit pores on the
@@
     \item Typically, separations are achieved based on size exclusion and
-    charge exclusion if the membrane surface is charged.
+    charge exclusion if the membrane's surface has a net charge.
     \item NF membranes require significantly less applied pressure in order
@@
   Nanostructured membranes attempt to overcome the permeability-selectivity 
-  tradeoff through molecular level design.
+  tradeoff through intelligent design at the molecular level.
   \begin{itemize}
@@
 
-  Graphene membranes are an extremely active are of research because 
-  they offer potential for extremely high permeability membranes.
+  Ultrathin-film graphene and graphene oxide membranes are a very active
+  area of research because they offer potential for extremely high 
+  permeability membranes.
   \begin{itemize}
-    \item 2D materials
-    \item Functionalization?
-    \item Easy to introduce defects
-    \item Multi-layered
+    \item An ideal graphene membrane is a 2D material consisting of a
+    single layer of graphene.\cite{humplik_nanostructured_2011}
+    \item Synthesis of a single layer of graphene at a large scale without
+    introducing defects is a challenge that has not yet been overcome.
+    \item Multilayered graphene membranes are a potentially easier and
+    more scalable technology which has garnered increasing interest in
+    recent years.\cite{cohen-tanugi_multilayer_2016,wei_multilayred_2018}
   \end{itemize}
 
-  Carbon nanotubes have shown promise due to unprecedentedly fast
-  water transport. 
+  Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes due
+  to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001} 
   \begin{itemize}
-    \item Functionalization of nanotubes
-    \item Aligned nanotubes difficult to synthesize
+    \item Practically, dispersing CNTs into a polymer matrix is extremely difficult
+    because they tend to agglomerate due to Van der Waals forces.
+    \item Functionalization of the CNT walls has been heavily investigated 
+    as a way to overcome this issue. 
+    \item Alignment of the CNTs into an array feasible as a nanoporous
+    membrane presents a further challenge to CNT membranes.\cite{sahoo_polymer_2010}
   \end{itemize}
@@
     \item Zeolites have highly uniform nm-sized crystalline structures with
-    cage-like cavities that allow movement and trapping of small solutes. \cite{pendergast_review_2011}
+    cage-like cavities that allow movement and trapping of small solutes. 
     \item The crystalline frameworks are typically formed by networks of silicon
@@
     overcome the permeability-selectivity tradeoff.
-    \item Most are prone to defects in the crystalline structure.
+    \item Most are prone to defects in the crystalline structure.\cite{pendergast_review_2011}
   \end{itemize}
@@
     \item LLCs are amphiphilic molecules that have the ability to self-assemble
-    into porous nanostructures \cite{smith_ordered_1997} and can be cross-linked
-    to create mechanically strong membrane films with periodic pores on the
-    order of 1 nm in diameter \cite{zhou_supported_2005}. 
-    \item LLC membrane pores are uniform in size because they are formed by 
-    self-assembly. 
+    into porous nanostructures\cite{smith_ordered_1997} that
+    can be cross-linked to create mechanically strong membrane films with 
+    periodic uniform-sized pores on the order of 1 nm in diameter \cite{zhou_supported_2005}. 
     \item Since LLC polymer membranes lack an appreciable pore size distribution,
@@
 
-  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:assembly}) has a
-  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
-  \begin{itemize}
-	  \item The H\textsubscript{II} phase forms at room temperature in the 
-	  presence of ca.~10 wt\% water and consists of hexagonally packed, 
-	  hydrophilic pore columns\cite{smith_ordered_1997}. 
-	  % BJC: should rethink the following since we think that thermotropic doesn't exist
-	  \item In the absence of water, neat monomer will form the same hexagonal
-	  columnar structure which, in the literature, has been referred to as the
-	  Col\textsubscript{h} thermotropic phase\cite{feng_scalable_2014}.
-  \end{itemize}
-
   Q\textsubscript{I}-phase membranes consist of a tortuous network of three
@@
 
+%  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:assembly}) has a
+%  high theoretical capacity for transport than the Q\textsubscript{I} phase.
+%  \begin{itemize}
+%	  \item The H\textsubscript{II} phase forms at room temperature in the 
+%	  presence of ca.~10 wt\% water and consists of hexagonally packed, 
+%	  hydrophilic pore columns\cite{smith_ordered_1997}. 
+%%	  \item The hexagonal, straight-pore geometry provides a dense array
+%%	  of hydrophilic channels and short pathways for solutes to travel.
+%	  % BJC: should rethink the following since we think that thermotropic doesn't exist
+%	  \item In the absence of water, neat monomer will form the same hexagonal
+%	  columnar structure which, in the literature, has been referred to as the
+%	  Col\textsubscript{h} thermotropic phase\cite{feng_scalable_2014}.
+%  \end{itemize}
+
   Recently, researchers have learned how to macroscopically align the
@@
     \item In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
-    domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
-	with subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
+    domains, a temperature-dependent hexagonal phase created by neat LLC monomers,
+    using a magnetic field with subsequent cross-linking to lock the structure 
+    in place\cite{feng_scalable_2014}.
 	\item In 2016, Feng et al.~showed that one could also obtain the same result
@@
 
-  Unfortunately, reproducing the work of Feng et al. with the H\textsubscript{II}
-  has been an experimental challenge. Therefore, the primary focus of experimental
-  research efforts has been with the Q\textsubscript{I} phase.
+  Unfortunately, reproducing the work of Feng et al. with the hydrated 
+  H\textsubscript{II} phase has been an experimental challenge. Therefore, the
+  primary focus of experimental research efforts has been with the Q\textsubscript{I} phase.
 
@@
 
-  A molecular-level understanding of structure of and transport in LLC polymer 
+  A molecular-level understanding of structure and transport in LLC polymer 
   membranes, enabled by molecular dynamics (MD) simulations, can provide 
@@
 
-  \noindent There are five primary objectives of our work.
+  \noindent There are four primary objectives of this PhD research.
   \begin{enumerate}
@@
     the role of monomer structure in solute transport and membrane design.
-    We will generate simulated X-ray diffraction patterns from MD trajectories
+    We will generate simulated X-ray diffraction (XRD) patterns from MD trajectories
     and compare them to an experimental 2D wide angle X-ray scattering (WAXS)
@@
 
-    \item Enable easy continuation of our work with a dedicated and 
-    well-documented python package.
-
-	Although molecular simulations have become popular
-	for studying systems at the atomic level, LLCs used in this context
-	have not been heavily investigated. Consequently, much of the 
-	analysis developed for this project is not widely applied. Therefore, 
-	it is important for us to make available the scripts that reproduce
-	the exact results presented in our published papers along with detailed
-	documentation of the scripts. This will ensure near-seamless continuation
-	of this project and accelerate the development of LLC membranes.
+%    \item Enable easy continuation of our work with a dedicated and 
+%    well-documented python package.
+%    
+%	Although molecular simulations have become popular
+%	for studying systems at the atomic level, LLCs used in this context
+%	have not been heavily investigated. Consequently, much of the 
+%	analysis developed for this project is not widely applied. Therefore, 
+%	it is important for us to make available the scripts that reproduce
+%	the exact results presented in our published papers along with detailed
+%	documentation of the scripts. This will ensure near-seamless continuation
+%	of this project and accelerate the development of LLC membranes.
 
@@
 
-  \textbf{\large Objective 1:} {\large Build and understand the nanoscopic structure of LLC membranes} (\textcolor{green!40!olive}{\textbf{Complete}})
+  \textbf{\large Objective 1:} {\large Build and understand the nanoscopic structure
+  of the H\textsubscript{II} phase} (\textcolor{green!40!olive}{\textbf{Complete}})
 
@@
     groups face towards the pore center.
-    \item We equilibrate the unit cell using a series of simulations
+    \item We did not add any water to the initial configuration because we
+    compared our structure to experimental data for a system claimed to be
+    synthesized dry.
+    \item We equilibrated the unit cell using a series of simulations
     with head groups held in place by position restraints. 
@@
     \item We carried out 400 ns equilibration simulations.
+
   \end{itemize}
@@
       \centering
-      \begin{subfigure}{.3\textwidth}
+      \begin{subfigure}{.325\textwidth}
               \centering
-              \includegraphics[width=\textwidth]{NaGA3C11.pdf}
+              \vspace{0.5cm}
+              \includegraphics[width=\textwidth]{NaGA3C11.pdf}  %BJC: can color code this once I figure out how
+              \vspace{0.05cm}
               \caption{}~\label{fig:monomer}
       \end{subfigure}
-      \begin{subfigure}{.3\textwidth}
-              \centering
-              \includegraphics[width=\textwidth]{monomer_twocolor.pdf}
-              \caption{}~\label{fig:atomistic_monomer}
-      \end{subfigure}
-      \begin{subfigure}{0.3\linewidth}
-              \centering
-              \includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
-              \caption{}~\label{fig:wedge}
-      \end{subfigure}
-              \begin{subfigure}{0.4\linewidth}
+%      \begin{subfigure}{.3\textwidth}
+%              \centering
+%              \includegraphics[width=\textwidth]{monomer_twocolor.pdf}
+%              \caption{}~\label{fig:atomistic_monomer}
+%      \end{subfigure}
+%      \begin{subfigure}{0.3\linewidth}
+%              \centering
+%              \includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
+%              \caption{}~\label{fig:wedge}
+%      \end{subfigure}
+              \begin{subfigure}{0.325\linewidth}
               \centering
@@
       \end{subfigure}
-      \begin{subfigure}{0.4\linewidth}
+      \begin{subfigure}{0.325\linewidth}
               \centering
@@
       \end{subfigure}
-      \caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
-      exhibits wedge-like character. (d) Monomers stack on top of each other to
-      create columns with short range order, then assemble into pores with
-      hydrophilic head groups (blue) facing towards the pore center. (e) The
-      pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
+      \caption{(a) The LLC monomer Na-GA3C11 exhibits wedge-like character. (b) 
+      Monomers stack on top of each other to create columns with short range order,
+      then assemble into pores with hydrophilic head groups (blue) facing towards 
+      the pore center. (c) The pores assemble into hexagonally packed columnar
+      mesophases.}~\label{fig:assembly}
   \end{figure}
@@
       \item We stacked monomers in parallel displaced and sandwiched 
-      configurations, two possible $\pi$-$\pi$ stacking modes.
+      configurations, two possible $\pi$-$\pi$ stacking modes.\cite{sinnokrot_estimates_2002}
       \item We also varied the initial distance between stacked monomers, $d$.
@@
   \noindent Our model's geometry is most consistent with experiment for systems
-  built with 5 columns per pore and monomers initially stacked 3.7 \AA apart
+  built with 5 columns per pore and monomers initially stacked 3.7 \AA~apart
   (see Figure~\ref{fig:p2p}). 
@@
     \item The pore spacing of 5 column-per-pore systems agree well with experiment.
-    \item 6 column-per-pore systems built with $d$ = 5 \AA appear to yield an
+    \item 6 column-per-pore systems built with $d$ = 5 \AA~appear to yield an
     experimentally consistent pore spacing however, the equilibrated distance
-    between stacked monomers stay close to 5 \AA which is inconsistent with 
+    between stacked monomers stay close to 5 \AA~which is inconsistent with 
     experiment. 
@@
     \item The five major reflections and the structural features leading
-    to them are summarized in Figure~\ref{fig:WAXS_comparison}.
+    to them are summarized and described in the caption of Figure~\ref{fig:WAXS_comparison}.
     \item Using MD trajectories, we simulated X-ray diffraction (XRD) 
@@
   \noindent It is necessary to add a small amount of water to our model in
-  order to fully reproduce all features of the WAXS pattern.
+  order to fully reproduce all features of the WAXS pattern (see 
+  Figure~\ref{fig:solvated_XRD}).
   \begin{itemize}
     \item We built our most experimentally consistent structure in the 
-    parallel displaced configuration with 1 wt \% water added to the 
+    parallel displaced configuration with 1 wt\% water added to the 
     pores. 
@@
     twice the $\pi$-stacking distance. 
+    \item The necessity of water in our model suggests that the membrane
+    synthesized by Feng et al. was slightly hydrated due to water molecules
+    leached from surroundings by the hydroscopic monomers. 
   \end{itemize}
@@
   %BJC: I think this is important to say somewhere
+  %BJC: but I don't have an ensemble of 1 wt % systems to fully prove that with.
+  %BJC: I could show cross-sections of R-pi, but that would require more context. 
   \noindent On the timescales that we can reasonably simulate, our model
@@
   \begin{subfigure}{\textwidth}
+  %BJC: probably change this legend to `d = x Angstroms` instead of 
+  % disordered/ordered, since I don't have space to talk about ordered / disorderd configurations (requires 
+  % nematic order parameter to give a complete justification of the names)
   \includegraphics[width=\textwidth]{regional_density_legend.pdf}
@@
 
-  \noindent We added additional water to our best Col\textsubscript{h} 
-  phase model in order to create the H\textsubscript{II} phase.
+  \noindent We added additional water to our most experimentally consistent
+  structural model in order to create a higher water content H\textsubscript{II}
+  phase model.
   \begin{itemize}
@@
     already fully hydrated at 7 wt \% water with additional water
-    trapped in defects between mesophases.
-    \item Therefore, we built two systems with 5 and 10 wt \% water.
+    trapped in defects between mesophases.\cite{resel_structural_2000}
+    \item Therefore, we built two systems with 5 and 10 wt\% water.
   \end{itemize}
@@
     greater than 1.5 nm from any pore center. 
-    \item There is an approximately 3:2 ratio of water in the pores to
+    \item There is approximately a 3:2 ratio of water in the pores to
     water in the distal tails. 
@@
   \noindent Water and sodium transport is significantly faster in the less
-  crowded 10 wt \% water pores. 
+  crowded 10 wt\% water pores. 
   \begin{itemize}
-    \item The MSD of water is about 51 times higher and the MSD of sodium is
-    about 49 times higher compared to 5 wt \% system.
+    \item The mean squared displacement (MSD) of water is about 51 times 
+    higher and the MSD of sodium is about 49 times higher compared to the 5 wt\% system.
     \item In general we observe similar solute transport mechanisms in the 5
-    and 10 wt \% water systems but at different time scales.
-    \item Therefore, we will focus on the 10 wt \% water system since we
-    can collect a larger quantity of mechanistic data from the solute 
-    trajectories.
+    and 10 wt\% water systems but on different time scales.
+    %BJC: might as well leave 5 wt% data in there.
+%    \item Therefore, we focus the remainder of this discussion on the 10 wt\%
+%    water system since we were able to collect a larger quantity of mechanistic
+%    data from the solute trajectories.
   \end{itemize}
 
+  % BJC: do you think I can get away with an appendix with the solute table + abbreviations that
+  % doesn't count towards the page limit?
   \noindent We observed transport of 20 different small polar solutes in the
@@
   \begin{itemize}
-    \item We created a separate initial configuration for each solute studied.
-    \item We placed 6 solutes, equally spaced in $z$, in each nanopore.
-    \item We allowed the solutes to simulate for 1 microsecond. 
+    \item We created a separate initial configuration for each solute studied and
+    placed 6 solutes, equally spaced in $z$, in each nanopore.
+    \item After a brief equilibration, we allowed the solutes to simulate for
+    1 microsecond. 
   \end{itemize}
 
-  \noindent The MSDs are not a monotonic function of solute size.
+  \noindent The solute MSDs are not a monotonic function of solute size.
   \begin{itemize}
@@
     \item We ensured that the Stokes-Einstein equation with the
-    correction factor of Gierer and Wirtz passed through methanol 
-    in order to give an approximate frame of reference. 
+    correction factor of Gierer and Wirtz\cite{gierer_molekulare_1953}
+    passed through methanol in order to give an approximate frame of reference. 
     \item Methanol is small and therefore can travel relatively
     unhindered compared to all other solutes.
+    \item The correction factor attempts to include the effects of
+    microfriction that begin to play a role when solute size becomes
+    on the order of solvent size.
     \item The theoretical line can be used as an approximate boundary
@@
     \item Figure~\ref{fig:hop_lengths} shows that this is the case for all solutes.
-    \item Hops made in the pore region are on average 45 \% larger than those made
+    \item Hops made in the pore region are on average 59 \% larger than those made
     outside the pore region.
@@
     \item For example, ribose spends the largest fraction of time in 
-    the pore center, but has the lowest hop frequency and the third 
+    the pore region, but has the fifth lowest hop frequency and the third 
     lowest average MSD (see Figures~\ref{fig:frac_time} and ~\ref{fig:hopfreq}).
@@
   \end{subfigure}
-  \caption{(a) Hops made in the pore region of the 10 wt \% water system
-  are, on average, 45 \% larger than those made outside the pore region.
+  \caption{(a) Hops made in the pore region of the 10 wt\% water system
+  are, on average, 59 \% larger than those made outside the pore region.
   The trend in hop lengths is similar to the trend in MSDs shown in
@@
   example, ribose spends the largest fraction of time in the pore region, yet
-  performs the the second lowest number of hops.}\label{fig:hops}
+  performs the the fifth lowest number of hops.}\label{fig:hops}
   \end{figure}
@@
     hydroxyl groups decreases.
+    \item Solutes with many hydroxyl groups, such as ribose, tetrose and 
+    glycerol, can donate multiple hydrogen bonds to monomer head groups 
+    simultaneously. 
+    \item When one hydrogen bond is broken, other hydrogen bonds work to
+    hold the solute in place, which allows broken hydrogen bonds to reform.
     \item Solutes that containing sulfur and nitrogen atoms in place of 
     oxygen atoms hydrogen bond less frequently since they are less 
-    electronegative elements.
+    electronegative elements. % citation
     \item The lifetime of hydrogen bonds follows nearly the same trend. Hydrogen
@@
   \begin{itemize}
-    \item The seven solutes that coordinate to sodium the most and 
-    the six solutes with the longest association dwell times all contain 
-    carbonyl groups, with the exception of DMSO which has an analagous sulfinyl group
-    (see Figures~\ref{fig:all_solutes_NA_coordination} and~\ref{fig:all_NA_dwells}).
+    \item Nearly all of the most coordinated solutes contain a carbonyl group 
+    (except for DMSO which has an analogous sulfinyl group). 
+    \item There is a significant drop in sodium ion association for solutes 
+    that do not contain carbonyl groups or multiple hydroxyl groups to compensate 
+    (see Figure~\ref{fig:all_solutes_NA_coordination}).
+    \item The corresponding dwell times follow a similar trend, however the dwell
+    times of highly coordinated solutes with multiple hydroxyl groups are generally
+    lower since association between hydroxyl groups and sodium is apparently a 
+    weaker interaction (Figure~\ref{fig:all_NA_dwells}).
 	\item Solutes with nitrogen atoms adjacent to the carbonyl groups tend to
@@
 
+  %BJC: This section will get developed further as I think about it more after the paper is submitted
   \noindent We are in the process of developing the theory required to build a 
@@
 
-  \noindent \textbf{\large Objective 5} \textit{\large Create a well-documented python package} (\textcolor{blue}{\textbf{In Progress}})
-
-  Python scripts used to simulate X-ray diffraction patterns are available in the following
-  GitHub repository: \url{https://github.com/joeyelk/MD-Structure-Factor}. Documentation
-  is forthcoming.
-
-  Python scripts used to conduct all other post-simulation trajectory analysis are 
-  also available on GitHub: \url{https://github.com/shirtsgroup/LLC_Membranes}. 
-  Documentation is a work in progress. It is available for viewing in its 
-  current state at \url{https://llc-membranes.readthedocs.io/en/latest/}.
+%  \noindent \textbf{\large Objective 5} \textit{\large Create a well-documented python package} (\textcolor{blue}{\textbf{In Progress}})
+%  
+%  Python scripts used to simulate X-ray diffraction patterns are available in the following
+%  GitHub repository: \url{https://github.com/joeyelk/MD-Structure-Factor}. Documentation
+%  is forthcoming. 
+%  
+%  Python scripts used to conduct all other post-simulation trajectory analysis are 
+%  also available on GitHub: \url{https://github.com/shirtsgroup/LLC_Membranes}. 
+%  Documentation is a work in progress. It is available for viewing in its 
+%  current state at \url{https://llc-membranes.readthedocs.io/en/latest/}.
 

### 2019-04-26 Ben_Manuscripts/transport/Draft.tex
updated draft.

@@
   anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
-  design of LLC monomers can help us tailor membranes for solute-specific
+  design of LLC monomers 
+  %MRS4: 
+  %can 
+  have the potential to 
+  help us tailor membranes for solute-specific
   separations.
@@
   selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
+  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
+  %separation BY size exclusion; maybe rephrase?
   While size-exclusion is a useful separation, it cannot reliably purify a 
@@
   unclear trends in experimental transport studies.~\cite{dischinger_effect_2017}
+  %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
+  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
 
   Molecular dynamics (MD) simulations can give us mechanistic insights with 
-  atomistic resolution so that we can directly observe small solute transport
+  atomistic resolution so that we can directly 
+  %MRS4: observe is strong, maybe describe? I'm open to other options.
+  % observe 
+  describe
+  small solute transport
   within LLC membrane nanopores and intelligently design new membranes for 
@@
 
-  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting
+  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting. 
+  %MRS4: I kind of like it here.  We can tweak the text to be a bit shorter without losing meaninig.
   In this work, we have studied the transport mechanisms exhibited by 20 
@@
   same time as protonated acetic acid.  
-
+  %MRS4: added for clarity
+  In any case, we are more interested in mechanisms of interaction with specific chemical functionality more than the behavior of specific molecules.
+
+%MRS4: probably shouldn't capitalize the names.  Maybe make the yellow a bit darker for the text.
 %  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
@@
   Previously, we have studied dry membrane systems and some systems with 
-  low water content. We will observe how the radial density of monomer 
+  low water content. We 
+  %MRS4: we already observed it
+  %will observe 
+  therefore first analyze 
+  how the radial density of monomer 
   components and water change within the pore based on membrane water content.
@@
   including water, partition within the pores. From a macroscopic perspective,
-  it is straightforward to hypothesize that the water and polar solutes spend
-  their time exclusively in the tube-like hydrophilic pore region. Our
+  %MRS4: tweak.
+  %it is straightforward 
+  it might make sense
+  to hypothesize that the water and polar solutes spend
+  their time exclusively in the tube-like hydrophilic pore region. 
+  %MRS4: However,
+  our
   previous work showed that there is a gradual compositional transition from
@@
 
-  For the remainder of the paper, we present our observations 
+  %MRS4:
+  %For 
+  In
+  the remainder of the paper, we present our observations 
   and explanations of the observed transport mechanisms exhibited by water
@@
 
-  There are also a couple of points that this study is not intended to address. 
+  There are also a couple of 
+  %points 
+  questions
+  that this study 
+  % is not intended to address. 
+  that are beyond the scope of this study.
   First, we will not study the concentration dependence of the observed transport
@@
   focused on the underlying solute-membrane interactions that lead to the 
-  observed transport mechanisms which we conjecture will be the same 
+  observed transport mechanisms which we conjecture will 
+  %MRS4: Some tone tweaks below.
+  %be 
+  remain roughly
+  the same 
   regardless of concentration. Second, we will not study the chemical potential
   of solutes in the pores, which could give us a better understanding of 
-  equilibrium solute partitioning. This information will not greatly enhance our
-  understanding of mechanistic details in various membrane regions. Both of the
-  above points will add unnecessary levels of complexity which can be left for
-  a future study. This work is a simple starting point meant for observing
+  equilibrium solute partitioning. However, this information 
+  %will not greatly enhance our
+  is not needed to 
+  understanding of mechanistic details in various membrane regions; 
+  %Both of the
+  %above points will add unnecessary levels of complexity which can be left for
+  %a future study. 
+  this work 
+  %is a simple 
+  represents
+  starting point for observing
   the types of interactions which occur between isolated solutes and the
@@
 
-  We observed that water partitions into the distal tail region of our system and therefore
+  We observed that 
+  %MRS4: added
+  some
+  water partitions into the distal tail region of our system and therefore
   built our initial configurations with water in both regions, close to the expected
@@
   insertion point we placed a randomly oriented solute molecule then ran a short 
-  energy minimization. We allowed the solutes to equilibrate for 5 ns using berendsen
+  energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
   pressure control then collected transport data over the course of 1 $\mu$s MD simulations.
-
+  %MRS4: Was Berendsen pressure control used for the transport as well?
+Should specify?
+I thought those might have been NVT?
+If so, should put in an acknowledgement that it's not quite right, cite my and Pascal's paper.
   \subsection{Solute Parameterization}\label{method:parameterization}
@@
   Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
-  We use GAFF since it has been parameterized for use with organic molecules. We
+  We use GAFF 
+  as it has been used extensively 
+  %since it has been parameterized 
+  for use with organic molecules.
+  We
   assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
@@
   where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
-  Generally, the MSD grows according to Equation~\ref{eqn:msd_form}:
+  %Generally, 
+  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
   \begin{equation} 
@@
   is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
-  by 2 (rather than 6) because we only measured the diffusion coefficient in one 
-  dimension.
+  by 2 (rather than 6) because we only measured 
+  %MRS4: check that this change is correct. 
+  %the diffusion coefficient 
+  particle displacement
+  in one dimension.
 
@@
   trends in solute MSDs, which is only valid because all trajectories are of the 
+  %MRS4: a bit strange to say you are using Stokes-einstein, but only analyzing MSD's (when MSD's don't appear in that equation)? It could be clarified a bit more.
   same length.
@@
   We reported the standard error in the average hop lengths by 
-  bootstrapping the hop lengths.
+  bootstrapping the 
+  %MRS4:
+  empirical distribution of observed
+  hop lengths.
   % BJC: could add more detail about which algorithm and cost function
   % penalty I used. Seems unnecessary since it is all in my code.
+  %MRS4: I would put in supporting.
 
@@
   calculated the 95\% confidence intervals of the distribution based
-  on its cumulative distribution function.
+  on the Poisson cumulative distribution function.
 
@@
   show that our conclusions are insensitive to this definition within a 
-  reasonable range.
-
+  reasonable range
+  %MRS4:added
+  of distances and angles.
   We determined the average percentage of solutes which actively participated
   in a hydrogen bond interaction with monomers each frame. We only counted
-  unique solute--monomer hydrogen bond interactions meaning solutes
+  unique solute--monomer hydrogen bond interactions, meaning solutes
   that hydrogen bond more than once simultaneously were classified as a
@@
   % use a percentile.
+  % MRS4: maybe while we are waiting for review.
   Hydrogen bond lifetimes appear to be distributed according to a power law or an
@@
   Due to memory limitations, we could not collect data frequently enough to provide a
-  sufficient answer to this question so we instead report the 95\textsuperscript{th} 
+  %MRS4: tweaking to 
+  sufficient answer to this question so when comparing solutes, we use the 95\textsuperscript{th} 
   percentile of hydrogen bond dwell times. This places emphasis on solutes with 
@@
   \caption{The radial densities of various monomer components paint a 
-  picture of the pore topology where the pore centers of hydrated systems are primarily composed
+  picture of the pore topology where the pore centers of hydrated systems are primarily,
+  %MRS4: added
+  but not exlusively,
+ composed
   of water and sodium ions. The monomer groups labeled in each plot correspond to 
@@
   for more water.}\label{fig:component_densities}
+  %MRS4: dotted horizontal line not defined.
   \end{figure}
 
+  %MRS4: this would be a good place to say that these waters won't be considered and why.
   There is an appreciable amount of water that partitions into the distal tail % BJC: defined in methods
@@
   the MSD of distal tail water decreases 8-fold. 
+  %MRS4: did it really decrease? From what?  What was the previous definision.
 
@@
   close to the pore center. The MSD of distal tail water molecules is 1.71 nm$^2$.
+  %MRS4: might not be clear to the reader what the consequence of this MSD value is above, since it's not compared to anything.
+  %MRS4: interesting the water in the tails is almost as fast as the water in the 10% weight. 
   This anomaly is likely a consequence of low density in the distal tails (see
   Figure~\ref{S-fig:total_density}) as well as structuring of water molecules via
-  hydrogen bonding. Water molecules are less likely to hydrogen bond while in the
+  hydrogen bonding. 
+  %MRS4: a bit confusing, since H-bonding occurs in both 10 and 5?
+Water molecules are less likely to hydrogen bond while in the
   distal tail region since they are interspersed between chains, while those in 
   the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
+  %MRS4: but there is also H-bonding to ions and carboxylate groups, which seems like they should be even stronger than water-water.
  hydrogen bonding between water molecules near the pore center versus those in 
@@
   of water molecules dominates.  
-
+  %MRS4: math seems a little inconsistent.  Does the tail water move the same rate in 5 and 10%? Seems like it should.
+  %MRS4: but above would tend to indicate that it moves 51/8 = 6.4 times faster in the tails in 10%? 
+  %MRS4: think about reading over/describiing the tail water here
+  %MRS4: would probably be useful to the reader to specify that we are neglecting transport in the tails here.
  \subsubsection{Transport of Small Polar Solutes}\label{section:general_transport_solutes}
@@
   environment within the nanopores rather than just solute size. Polar solutes
-  are slowed by interactions between monomer functional groups and ions. Solutes
+  are slowed by interactions between monomer functional groups and ions. 
+  %MRS4: sentence here seems like out of scope for the section title. 
+  Solutes
   with hydrophobic character partition out of the pore and are slowed by densely
-  packed organic monomer components. A thorough understanding of these interactions
+  packed organic monomer components. 
+  %MRS4: this above seems like a general statement for all transport, not just small polar solutes?
+Should there be a bit of an introduction to transport as a whole before going into specific molecular classes?
+  A thorough understanding of these interactions
   will help us to create monomer design principles. We will begin our analysis by
@@
   against their MSD in Figures~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
-  Of all the solutes, we believe methanol is subject to the least hindrance by
+  Of all the solutes, %we believe 
+  methanol 
+  %MRS4:
+  %added
+  likely
+  is subject to the least hindrance by
   the membrane due its small size. Therefore we fit Equation~\ref{eqn:stokes-einstein}
-  so that it intersected methanol's MSD. The uncorrected version of 
+  so that it intersects methanol's MSD. 
+  %MRS4: intersect where?  Might not be clear to readers that next sentence is a continuation of the process in the sentence above.
+  The uncorrected version of 
   Equation~\ref{eqn:stokes-einstein} ($f$=1) is plotted and converges to the same value as the
@@
   Overall, the transport behavior exhibited by solutes in the 5 wt\% water
-  systems is similar to that shown by those in the 10 wt\% system however
+  systems is similar to that shown by those in the 10 wt\% system; however
   the timescales are much longer. We observe subdiffusive behavior with 
@@
   \end{subfigure}
+  %MRS4: suggest putting something at the beginning of the caption indicating which chemical group it is.
   \caption{(a) The MSD of the simple alcohols decrease as a function of the
@@
   The order of the MSDs of solutes in this grouping are roughly consistent with 
-  their size, however propylene glycol moves exceptionally slow (see 
+  their size; however, propylene glycol moves exceptionally slowly (see 
   Figure~\ref{fig:polyols_msd}). Ethylene glycol has the highest MSD followed
@@
   fraction of their time in the pore region than any other solute (see 
-  Figure~\ref{fig:frac_time}) This is likely a consequence of both their 
+  Figure~\ref{fig:frac_time}). This is likely a consequence of both their 
   hydrophilicity and large size which prevents them from partitioning into the 
@@
   \end{subfigure}
+  %MRS4: suggest cutting off the density in height at 1.0, so that the scales of the other molecules can be seen.
+  %MRS4: below - specify which set this is.
   \caption{(a) The MSDs of the solutes in this set descend in order of their size, except
@@
   a carbonyl group with two attached heavy atoms. All are similar in size and
-  are planar molecules due to the sp2 hybridization of their carbonyl group. 
+  are planar molecules due to the $sp^2$ hybridization of their carbonyl group. 
   The fastest solutes of this grouping, acetic acid and urea, move about 3
@@
   solute MSD. Peaks in the RDFs of urea, acetamide and acetone that appear 
-  0.2 - 0.4 nm from the pore center are likely due to coordination with sodium
+  0.2 - 0.4 nm from the pore center are 
+  %MRS4: seems like we could make it stronger with ``likely do''?
+  likely due to coordination with sodium
   ions. (c) The amides hydrogen bond with water far less than acetic acid, 
@@
   ion may offer some interesting behavior. 
-
+  %MRS4: abrupt ending . . . think about a better way to wrap up that focuses on what was learned as well.
   %BJC: future work? i.e. talk about mathematical modeling 
+  %MRS4: the modeling is scietifically a bit different.  MAybe nto
 

### 2019-04-26 Ben_Manuscripts/transport/Draft.tex
Draft updates

@@
 \SectionNumbersOn
+%\definecolor{amber}{rgb}{1.0, 0.75, 0.0} % amber
+%\definecolor{amber}{rgb}{1.0, 0.84, 0.0} % gold
+\definecolor{amber}{rgb}{0.99, 0.76, 0.0} % golden poppy
 
@@
   anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
-  design of LLC monomers 
-  %MRS4: 
-  %can 
-  have the potential to 
-  help us tailor membranes for solute-specific
-  separations.
+  design of LLC monomers have the potential to help us tailor membranes for 
+  solute-specific separations.
 
@@
   in a lab setting, there is a limit to the level of detail that can be obtained 
-  from experiment. The separation performance of these membranes has been 
+  from experiment. 
+%  These membranes have been primarily characterized with size-exclusion experiments
+%  which can give an estimate of pore size as well as selectivity based on differences
+%  in solute sizes~\cite{zhou_supported_2005}.  
+  The separation performance of these membranes has been 
   primarily characterized with size-exclusion experiments which emphasizes 
@@
   %separation BY size exclusion; maybe rephrase?
-  While size-exclusion is a useful separation, it cannot reliably purify a 
-  solution where the solute size is on the same order as water. Therefore, it is
+  %BJC4: Hmm, by characerization, I mean testing their ability to separate, so I'm 
+  While size-exclusion is a useful separation, it 
+  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
   important to take advantage of material properties other than pore size. 
-  Unfortunately, interactions between solutes and pore moieties have yielded
-  unclear trends in experimental transport studies.~\cite{dischinger_effect_2017}
+  Unfortunately, this is a more complicated design problem. Experimental transport
+  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
+  unclear trends due to interactions between solutes and pore moieties. Although
+  the authors identified some correlation between select physicochemical properties
+  and solute transport trends, their empirical model does not offer a sufficient 
+  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
   %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
   % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
+  %BJC4: gave it another shot above.
 
   Molecular dynamics (MD) simulations can give us mechanistic insights with 
-  atomistic resolution so that we can directly 
-  %MRS4: observe is strong, maybe describe? I'm open to other options.
-  % observe 
-  describe
-  small solute transport
-  within LLC membrane nanopores and intelligently design new membranes for 
+  atomistic resolution so that we can provide detailed descriptions of
+  small solute transport within LLC membrane nanopores and intelligently design new membranes for 
   solute-specific separations. In our previous work, we used MD simulations to 
@@
 
-  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting. 
-  %MRS4: I kind of like it here.  We can tweak the text to be a bit shorter without losing meaninig.
   In this work, we have studied the transport mechanisms exhibited by 20 
@@
   to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
-  same time as protonated acetic acid.  
-  %MRS4: added for clarity
-  In any case, we are more interested in mechanisms of interaction with specific chemical functionality more than the behavior of specific molecules.
+  same time as protonated acetic acid. In any case, we are more interested 
+  in mechanisms of interaction with specific chemical functionality more than 
+  the behavior of specific molecules.
 
 %MRS4: probably shouldn't capitalize the names.  Maybe make the yellow a bit darker for the text.
-%  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
-%  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
-%  % them much thought. Just used their residue names
-%  \begin{table}
-%  \centering
-%  \begin{tcolorbox}[%
-%  	colframe=blue,
-%  	title=\centering \textbf{Solute Names and Their Abbreviations},
-%  	width=0.7\textwidth,
-%  	box align=center,
-%  	halign=center,
-%  	valign=center,
-%  	fontupper=\linespread{1}\selectfont]
-%
-%  \begin{multicols}{2}
-%
-%  \textbf{Name} \\
-%  Acetic Acid \\
-%  Acetamide \\
-%  Acetone \\
-%  Butanol \\
-%  Dimethyl Formamide \\
-%  2,3-Dimercapto-1-propanol \\
-%  Dimethyl Sulfoxide \\
-%  Ethyl Acetate \\ 
-%  Ethanol \\
-%  Ethylene Glycol \\
-%  Glycerol \\
-%  Methanol \\ 
-%  Propylene Carbonate \\
-%  Propylene Glycol \\
-%  Propanol \\
-%  Ribose \\
-%  Mercaptoethanol \\
-%  Tetrose \\
-%  Tetrahydrofuran \\
-%  Urea \\
-%  \columnbreak
-%
-%  \textbf{Abbrevation} \\
-%  AcOH \\  % Acetic acid
-%  AcN \\  % Acetamide
-%  ACE \\  % Acetone
-%  BtOH \\  % Butanol
-%  DMF \\  % Dimethyl Formamide
-%  DMP \\  % 2,3-Dimercapto-1-propanol
-%  DMSO \\  % Dimethyl sulfoxide
-%  ETAC \\  % Ethyl Acetate
-%  EtOH \\  % ethanol
-%  EG \\  % ethylene glycol
-%  GLY \\  % glycerol
-%  MeOH \\  % methanol
-%  PC \\ % propylene carbonate
-%  PG \\  % propylene glycol
-%  PrOH \\  % propanol
-%  RIB \\ 
-%  ME \\ % mercaptoethanol
-%  TET \\
-%  THF \\ 
-%  URE \\
-%  
-%  \end{multicols}
-%  
-%  %MRS2: can you put molecules in the table as well?
-I think it would be better for reference.
-Some of the larger ones may have small molecules.
-You can potentially partially stagger them horizontally so the size can be OK?
-%  \end{tcolorbox}
-%  \caption{}\label{table:abbreviations}
-%  \end{table}
+%BJC4: tried a new yellow. I think it's more readable. Hard to say
 
@@
     \hline
-	\color{blue}{Methanol} & \color{blue}{MeOH} &     
+	\color{blue}{methanol} & \color{blue}{MeOH} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{green!40!olive}{Urea} & \color{green!40!olive}{URE} &     
+    \color{green!40!olive}{urea} & \color{green!40!olive}{URE} &     
     \begin{minipage}{.1\textwidth}
@@
 
-   	\color{blue}{Ethanol} & \color{blue}{EtOH} &     
+   	\color{blue}{ethanol} & \color{blue}{EtOH} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{green!40!olive}{Acetamide} & \color{green!40!olive}{AcN} &     
+    \color{green!40!olive}{acetamide} & \color{green!40!olive}{AcN} &     
     \begin{minipage}{.1\textwidth}
@@
 
-  	\color{blue}{Propanol} & \color{blue}{PrOH} &     
+  	\color{blue}{propanol} & \color{blue}{PrOH} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{green!40!olive}{Acetone} & \color{green!40!olive}{ACE} &     
+    \color{green!40!olive}{acetone} & \color{green!40!olive}{ACE} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{blue}{Butanol} & \color{blue}{BtOH} &     
+    \color{blue}{butanol} & \color{blue}{BtOH} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{orange}{Mercaptoethanol} & \color{orange}{ME} &     
+    \color{orange}{mercaptoethanol} & \color{orange}{ME} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{Ethylene Glycol} & \color{red}{EG} &     
+    \color{red}{ethylene glycol} & \color{red}{EG} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{orange}{Dimethyl Sulfoxide} & \color{orange}{DMSO} &     
+    \color{orange}{dimethyl sulfoxide} & \color{orange}{DMSO} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{Propylene Glycol} & \color{red}{PG} &     
+    \color{red}{propylene glycol} & \color{red}{PG} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{orange}{2,3-Dimercapto-1-propanol} & \color{orange}{DMP} &     
+    \color{orange}{2,3-dimercapto-1-propanol} & \color{orange}{DMP} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{Glycerol} & \color{red}{GLY} &     
+    \color{red}{glycerol} & \color{red}{GLY} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{yellow!70!orange}{Tetrahydrofuran} & \color{yellow!70!orange}{THF} &     
+    \color{amber}{tetrahydrofuran} & \color{amber}{THF} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{Tetrose} & \color{red}{TET} &     
+    \color{red}{tetrose} & \color{red}{TET} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{yellow!70!orange}{Dimethylformamide} & \color{yellow!70!orange}{DMF} &     
+    \color{amber}{dimethylformamide} & \color{amber}{DMF} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{Ribose} & \color{red}{RIB} &     
+    \color{red}{ribose} & \color{red}{RIB} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{yellow!70!orange}{Propylene Carbonate} & \color{yellow!70!orange}{PC} &     
+    \color{amber}{propylene carbonate} & \color{amber}{PC} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{green!40!olive}{Acetic Acid} & \color{green!40!olive}{AcOH} &     
+    \color{green!40!olive}{acetic acid} & \color{green!40!olive}{AcOH} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{yellow!70!orange}{Ethyl Acetate} & \color{yellow!70!orange}{EAC} &     
+    \color{amber}{ethyl acetate} & \color{amber}{EAC} &     
     \begin{minipage}{.1\textwidth}

### 2019-04-30 Ben_Manuscripts/transport/Draft.tex
Updates
Text fixes and updates to errorbars

@@
 
-  Membranes capable of separating nm-sized solutes with high selectivity 
-  and permeability are highly desirable for a number of applications. For 
-  example, separation of salt from seawater or other briny sources can 
-  yield potable drinking water.~\cite{fritzmann_state---art_2007} Removal
-  of organic micropollutants, such as personal care products, pesticides
-  and pharmaceuticals, from surface and groundwaters, can have large benefits
-  for public health.~\cite{schwarzenbach_challenge_2006} Finally,
-  one can purify and recover dissolved species present in complex
-  hydraulic fracturing flowback water waste streams which would help mitigate
-  the effects of deep well injection and can be sold for profit.~\cite{dischinger_application_2017}
-
-  All of these separations are possible in part with current commercial membrane
-  separation techniques but suffer from serious drawbacks. Currently, reverse 
-  osmosis (RO) and nanofiltration (NF) dominate commercial membrane separations
-  of small molecules.~\cite{warsinger_review_2018} RO membranes are typically
-  dense polymer matrices that separate solutes based on differences in their
-  solubility and permeability in the membrane material.~\cite{fritzmann_state---art_2007}
-  Although they can perform highly selective separations, high feed pressures,
-  and thus large amounts of energy, are necessary in order to generate a 
-  useful permeate flux.~\cite{van_der_bruggen_review_2003} NF membranes have 
-  well-defined nm-sized pores which can give the same permeate flux as RO
-  with lower applied pressure.~\cite{hilal_comprehensive_2004} However, the 
-  pores are not uniform in size, limiting selectivity.~\cite{werber_materials_2016}.
+  Membranes capable of separating nm-sized solutes with high selectivity and
+  permeability are highly desirable for a number of applications. For example,
+  separation of salt from seawater or other briny sources can yield potable
+  drinking water.~\cite{fritzmann_state---art_2007} Removal of organic
+  micropollutants, such as personal care products, pesticides and
+  pharmaceuticals, from surface and groundwaters, can have large benefits for
+  public health.~\cite{schwarzenbach_challenge_2006} Finally, one can purify and
+  recover dissolved species present in complex hydraulic fracturing flowback
+  water waste streams which would help mitigate the effects of deep well
+  injection and can be sold for profit.~\cite{dischinger_application_2017}
+
+  All of these separations are possible in part with current commercial
+  membrane separation techniques but suffer from serious drawbacks. Currently,
+  reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
+  separations of small molecules.~\cite{warsinger_review_2018} RO membranes are
+  typically dense polymer matrices that separate solutes based on differences in
+  their solubility and permeability in the membrane
+  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
+  selective separations, high feed pressures, and thus large amounts of energy,
+  are necessary in order to generate a useful permeate
+  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
+  nm-sized pores which can give the same permeate flux as RO with lower applied
+  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
+  size, limiting selectivity.~\cite{werber_materials_2016}.
 %  Therefore, multiple membrane passes may be necessary in order to achieve 
@@
   in a lab setting, there is a limit to the level of detail that can be obtained 
-  from experiment. 
-%  These membranes have been primarily characterized with size-exclusion experiments
-%  which can give an estimate of pore size as well as selectivity based on differences
-%  in solute sizes~\cite{zhou_supported_2005}.  
-  The separation performance of these membranes has been 
-  primarily characterized with size-exclusion experiments which emphasizes 
-  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
-  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
-  %separation BY size exclusion; maybe rephrase?
-  %BJC4: Hmm, by characerization, I mean testing their ability to separate, so I'm 
-  While size-exclusion is a useful separation, it 
-  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
-  important to take advantage of material properties other than pore size. 
-  Unfortunately, this is a more complicated design problem. Experimental transport
-  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
-  unclear trends due to interactions between solutes and pore moieties. Although
-  the authors identified some correlation between select physicochemical properties
-  and solute transport trends, their empirical model does not offer a sufficient 
-  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
+  from experiment. These membranes have been primarily characterized with 
+  size-exclusion experiments which can give an estimate of pore size as well as
+  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
+  However, size exclusion does not appear to be sufficient to fully describe LLC
+  membranes. Dischinger et al. studied a similar membrane and found that they do
+  not separate purely on the basis of size. Empirical modeling revealed correlations
+  between various solute physicochemical properties and observed solute rejection. 
+  Although there was some agreement with their empirical model, it does not
+  offer a sufficiently detailed explanation of governing molecular interactions.
+  ~\cite{dischinger_effect_2017}
+
+%  The separation performance of these membranes has been 
+%  primarily characterized with size-exclusion experiments which emphasizes 
+%  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
+%  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
+%  %separation BY size exclusion; maybe rephrase?
+%  %BJC4: Hmm, by characerization, I mean testing their ability to separate, so I'm 
+%  While size-exclusion is a useful separation, it 
+%  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
+%  important to take advantage of material properties other than pore size. 
+%  Unfortunately, this is a more complicated design problem. Experimental transport
+%  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
+%  unclear trends due to interactions between solutes and pore moieties. Although
+%  the authors identified some correlation between select physicochemical properties
+%  and solute transport trends, their empirical model does not offer a sufficient 
+%  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
   %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
   % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
-  %BJC4: gave it another shot above.
 
@@
 
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ortho_view.pdf}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{top_view.pdf}
+  \caption{}
+  \end{subfigure}
+  \caption{In both figures, water molecules that occupy the pores are colored blue,
+  the hydrophilic head groups of the LLC monomers are colored orange with all else
+  colored gray. (a) Membrane pores are approximately straight and (b) are packed 
+  hexagonally.}\label{fig:membrane_rendering}
+  \end{figure}
+
   In this work, we have studied the transport mechanisms exhibited by 20 
   uncharged polar solutes with varying size, chemical functionality and hydrophilic 
-  character. We have listed the solutes studied along with the abbreviations that
+  character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
+  the membrane in which solutes are placed. 
+  We have listed the solutes studied along with the abbreviations that
   we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
@@
 
-%MRS4: probably shouldn't capitalize the names.  Maybe make the yellow a bit darker for the text.
-%BJC4: tried a new yellow. I think it's more readable. Hard to say
-
   \begin{table}[h!]
@@
     \hline
-	\color{blue}{methanol} & \color{blue}{MeOH} &     
+	\color{blue}{\textbf{methanol}} & \color{blue}{\textbf{MeOH}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{green!40!olive}{urea} & \color{green!40!olive}{URE} &     
+    \color{green!40!olive}{\textbf{urea}} & \color{green!40!olive}{\textbf{URE}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-   	\color{blue}{ethanol} & \color{blue}{EtOH} &     
+   	\color{blue}{\textbf{ethanol}} & \color{blue}{\textbf{EtOH}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{green!40!olive}{acetamide} & \color{green!40!olive}{AcN} &     
+    \color{green!40!olive}{\textbf{acetamide}} & \color{green!40!olive}{\textbf{AcN}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-  	\color{blue}{propanol} & \color{blue}{PrOH} &     
+  	\color{blue}{\textbf{propanol}} & \color{blue}{\textbf{PrOH}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{green!40!olive}{acetone} & \color{green!40!olive}{ACE} &     
+    \color{green!40!olive}{\textbf{acetone}} & \color{green!40!olive}{\textbf{ACE}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{blue}{butanol} & \color{blue}{BtOH} &     
+    \color{blue}{\textbf{butanol}} & \color{blue}{\textbf{BtOH}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{orange}{mercaptoethanol} & \color{orange}{ME} &     
+    \color{orange}{\textbf{mercaptoethanol}} & \color{orange}{\textbf{ME}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{ethylene glycol} & \color{red}{EG} &     
+    \color{red}{\textbf{ethylene glycol}} & \color{red}{\textbf{EG}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{orange}{dimethyl sulfoxide} & \color{orange}{DMSO} &     
+    \color{orange}{\textbf{dimethyl sulfoxide}} & \color{orange}{\textbf{DMSO}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{propylene glycol} & \color{red}{PG} &     
+    \color{red}{\textbf{propylene glycol}} & \color{red}{\textbf{PG}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{orange}{2,3-dimercapto-1-propanol} & \color{orange}{DMP} &     
+    \color{orange}{\textbf{2,3-dimercapto-1-propanol}} & \color{orange}{\textbf{DMP}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{glycerol} & \color{red}{GLY} &     
+    \color{red}{\textbf{glycerol}} & \color{red}{\textbf{GLY}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{amber}{tetrahydrofuran} & \color{amber}{THF} &     
+    \color{amber}{\textbf{tetrahydrofuran}} & \color{amber}{\textbf{THF}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{tetrose} & \color{red}{TET} &     
+    \color{red}{\textbf{tetrose}} & \color{red}{\textbf{TET}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{amber}{dimethylformamide} & \color{amber}{DMF} &     
+    \color{amber}{\textbf{dimethylformamide}} & \color{amber}{\textbf{DMF}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{red}{ribose} & \color{red}{RIB} &     
+    \color{red}{\textbf{ribose}} & \color{red}{\textbf{RIB}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{amber}{propylene carbonate} & \color{amber}{PC} &     
+    \color{amber}{\textbf{propylene carbonate}} & \color{amber}{\textbf{PC}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{green!40!olive}{acetic acid} & \color{green!40!olive}{AcOH} &     
+    \color{green!40!olive}{\textbf{acetic acid}} & \color{green!40!olive}{\textbf{AcOH}} &     
     \begin{minipage}{.1\textwidth}
@@
 
-    \color{amber}{ethyl acetate} & \color{amber}{EAC} &     
+    \color{amber}{\textbf{ethyl acetate}} & \color{amber}{\textbf{EAC}} &     
     \begin{minipage}{.1\textwidth}
@@
   solutes and yellow to solutes that can only accept hydrogen bonds but not donate.}\label{table:abbreviations}
-  % BJC: achemso for jpcb makes table captions bold
-  % BJC: also, it's published that way
   \end{table}
@@
   Previously, we have studied dry membrane systems and some systems with 
-  low water content. We 
-  %MRS4: we already observed it
-  %will observe 
-  therefore first analyze 
-  how the radial density of monomer 
+  low water content. We therefore first analyze how the radial density of monomer 
   components and water change within the pore based on membrane water content.
@@
   including water, partition within the pores. From a macroscopic perspective,
-  %MRS4: tweak.
-  %it is straightforward 
-  it might make sense
-  to hypothesize that the water and polar solutes spend
-  their time exclusively in the tube-like hydrophilic pore region. 
-  %MRS4: However,
-  our
+  it might make sense to hypothesize that the water and polar solutes spend
+  their time exclusively in the tube-like hydrophilic pore region. Our
   previous work showed that there is a gradual compositional transition from
@@
 
-  %MRS4:
-  %For 
-  In
-  the remainder of the paper, we present our observations 
+  In the remainder of the paper, we present our observations 
   and explanations of the observed transport mechanisms exhibited by water
@@
 
-  There are also a couple of 
-  %points 
-  questions
-  that this study 
-  % is not intended to address. 
-  that are beyond the scope of this study.
-  First, we will not study the concentration dependence of the observed transport
+  There are also a couple of questions that this study that are beyond the 
+  scope of this study. First, we will not study the concentration dependence of the observed transport
   rates. Although the average MSD might change with concentration, we are 
   focused on the underlying solute-membrane interactions that lead to the 
-  observed transport mechanisms which we conjecture will 
-  %MRS4: Some tone tweaks below.
-  %be 
-  remain roughly
-  the same 
-  regardless of concentration. Second, we will not study the chemical potential
+  observed transport mechanisms which we conjecture will remain roughly
+  the same regardless of concentration. Second, we will not study the chemical potential
   of solutes in the pores, which could give us a better understanding of 
-  equilibrium solute partitioning. However, this information 
-  %will not greatly enhance our
-  is not needed to 
-  understanding of mechanistic details in various membrane regions; 
-  %Both of the
-  %above points will add unnecessary levels of complexity which can be left for
-  %a future study. 
-  this work 
-  %is a simple 
-  represents
-  starting point for observing
-  the types of interactions which occur between isolated solutes and the
-  membrane.
+  equilibrium solute partitioning. However, this information is not needed
+  to understand the mechanistic details in various membrane regions; 
+  This work represents a starting point for observing the types of interactions
+  which occur between isolated solutes and the membrane.
 
@@
 
-  We observed that 
-  %MRS4: added
-  some
-  water partitions into the distal tail region of our system and therefore
+  We observed that some water partitions into the distal tail region of our system and therefore
   built our initial configurations with water in both regions, close to the expected
@@
   energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
-  pressure control then collected transport data over the course of 1 $\mu$s MD simulations.
-  %MRS4: Was Berendsen pressure control used for the transport as well?
-Should specify?
-I thought those might have been NVT?
-If so, should put in an acknowledgement that it's not quite right, cite my and Pascal's paper.
+  pressure control then collected transport data over the course of 1 $\mu$s MD simulations
+  with pressure controlled by the Parrinello-Rahman barostat.
+
   \subsection{Solute Parameterization}\label{method:parameterization}
@@
   Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
-  We use GAFF 
-  as it has been used extensively 
-  %since it has been parameterized 
-  for use with organic molecules.
-  We
-  assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
+  We use GAFF as it has been used extensively for use with organic molecules.
+  We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
   with QUACPAC from Openeye Scientific Software.
@@
   where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
-  %Generally, 
   The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
@@
   is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
-  by 2 (rather than 6) because we only measured 
-  %MRS4: check that this change is correct. 
-  %the diffusion coefficient 
-  particle displacement
-  in one dimension.
+  by 2 (rather than 6) because we only measured particle displacement in one dimension.
 
@@
   \end{equation}
-  For consistency with the presentation of our results, rather than calculate trends
-  in $D$, we will apply Equation~\ref{eqn:stokes-einstein} in order to analyze 
-  trends in solute MSDs, which is only valid because all trajectories are of the 
+  For consistency with the presentation of our results, rather than calculate 
+  trends in $D$, we will calculate trends in trends in solute MSDs. For Brownian
+  particles, $D$ is proportional to the MSD divided by time, $t$. Therefore, 
+  we analyze qualitative trends in solute MSDs according to:
+  \begin{equation}
+  MSD = \dfrac{k_bTt}{6\pi\eta fr}
+  \label{eqn:msd-stokes-einstein}
+  \end{equation}
+  We hold $t$ constant in our simulations in order to make side-by-side comparisons.
+
   %MRS4: a bit strange to say you are using Stokes-einstein, but only analyzing MSD's (when MSD's don't appear in that equation)? It could be clarified a bit more.
-  same length.
 %  However, this assumes linear behavior
@@
 
-  Since we will be using this equation for primarily qualitative observations, 
+  Since we will be using Equation~\ref{eqn:msd-stokes-einstein} for primarily qualitative observations, 
   we made a number of simplifying assumptions so that it could easily be used for 
@@
 
-  In order to make qualitative comparisons, we fit Equation~\ref{eqn:stokes-einstein}
+  %BJC: another option is to fit to water which IS Brownian in the 10 wt% system.
+  In order to make qualitative comparisons, we fit Equation~\ref{eqn:msd-stokes-einstein}
   so that it passed through the highest solute MSD. We assumed that the solute
-  with the highest MSD behaved the most ``Stokes-like" and therefore could set a
-  rough boundary between subdiffusive, Brownian and superdiffusive MSDs. As a lower
+  with the highest MSD exhibited the closest to Brownian behavior and therefore could set
+  a rough boundary between subdiffusive, Brownian and superdiffusive MSDs. As a lower
   bound to our appoximation, we also plotted the uncorrected version of 
@@
   We reported the standard error in the average hop lengths by 
-  bootstrapping the 
-  %MRS4:
-  empirical distribution of observed
-  hop lengths.
+  bootstrapping the empirical distribution of observed
+  hop lengths.\cite{efron_introduction_1994}
   % BJC: could add more detail about which algorithm and cost function
@@
 
-  We determined the frequency of hops by dividing the total number of 
-  hops by the total length of the simulation. We used the average
-  frequency as the $\lambda$ parameter in a Poisson distribution. We
-  calculated the 95\% confidence intervals of the distribution based
-  on the Poisson cumulative distribution function.
+  We determined the average frequency of hops by dividing the total number of 
+  hops by the total length of the simulation. We used the frequency of
+  hops per 1000 ns as the $\lambda$ parameter in a Poisson distribution.
+  We calculated the 1--$\sigma$ confidence intervals of the probability % BJC: not sure best way to write 1-sigma CI
+  distribution of hops per 1000 ns based on the corresponding Poisson 
+  cumulative distribution function and scaled them to a per--nanosecond basis.
 
@@
   show that our conclusions are insensitive to this definition within a 
-  reasonable range
-  %MRS4:added
-  of distances and angles.
-  We determined the average percentage of solutes which actively participated
-  in a hydrogen bond interaction with monomers each frame. We only counted
-  unique solute--monomer hydrogen bond interactions, meaning solutes
-  that hydrogen bond more than once simultaneously were classified as a
+  reasonable range of distances and angles. We determined the average percentage
+  of solutes which actively participated in a hydrogen bond interaction with 
+  monomers each frame. We only counted unique solute--monomer hydrogen bond 
+  interactions, meaning solutes that hydrogen bond more than once simultaneously were classified as a
   single pairing event. We determined the standard error of this calculation
@@
   normalized by the volume of the annulus defined by the bin edges.
+  We generated 1-$\sigma$ confidence intervals by bootstrapping the 
+  RDFs of each individual solute 200 times. For each solute, we obtained
+  an RDF averaged over the entire simulation trajectory. We randomly 
+  chose solute RDFs with replacement and averaged them for each bootstrap
+  trial. This approach assumes that solute positions are uncorrelated to
+  other solutes which we believe is valid due to the low degree of 
+  interaction between solutes described in Section~\ref{method:system_setup}.
+
   Although the pores are often described as straight, they have a
@@
   calculated based on the closest two spline points. Using the splines, 
-  % BJC: below to supporting?
   we calculated the tortuosity of the pores by calculating the ratio 
@@
 
-  In all RDF plots, we include the average RDF of the head groups as
-  a reference. The head group RDF shown is the average of the head 
-  group RDFs for each solute system in the plot. We generated 
-  95\% confidence intervals by bootstrapping the RDF of each individual
-  head group. For each head group, we obtained an RDF averaged over the
-  entire simulation trjaectory. We randomly chose head group RDFs with replacement
-  and averaged them for each bootsrap trial. This approach assumes that
-  head group positions are uncorrelated.
+  In all RDF plots, we include the average RDF of the head groups as a 
+  reference. The head group RDF shown is the average of the head group
+  RDFs for each solute system in the plot. We generated 1-$\sigma$ 
+  confidence intervals by bootstrapping the RDFs in the same way we did
+  the solutes. We scaled the head group RDF so that it would be visible
+  next to solute RDFs.
+
+%  of each individual
+%  head group. For each head group, we obtained an RDF averaged over the
+%  entire simulation trajactory. We randomly chose head group RDFs with replacement
+%  and averaged them for each bootsrap trial. This approach assumes that
+%  head group positions are uncorrelated.
 
@@
   picture of the pore topology where the pore centers of hydrated systems are primarily,
-  %MRS4: added
-  but not exlusively,
- composed
-  of water and sodium ions. The monomer groups labeled in each plot correspond to 
+  but not exclusively, composed of water and sodium ions. The monomer groups labeled in each plot correspond to 
   the color-coded monomer pictured in the upper right corner of the figure. 
@@
   pore center normalized by the volume of the annular bin to which they belong.
+  The vertical dashed black lines are positioned so that they intersect with 
+  the maximum head group density.
   (a) In the dry system, the density of head groups and sodium ions are highest
-  within 0.25 nm of the pore center. (b) In the 5 wt\% system, monomer head 
-  groups retreat about 0.2 nm radially in order to make room for water molecules.
+  0.15 to 0.4 nm from the pore center. There is an appreciable density of head groups
+  crowding the pore center (b) In the 5 wt\% system, monomer head 
+  groups retreat radially in order to make room for water molecules at the pore center.
   (c) Monomers in the 10 wt\% system retreat an additional 0.2 nm to make room
@@
 
-  %MRS4: this would be a good place to say that these waters won't be considered and why.
   There is an appreciable amount of water that partitions into the distal tail % BJC: defined in methods
@@
 
+  % Changing pore radius does not change conclusion here.
+  In the 5 wt\% water system, water molecules that spend the majority of their 
+  time in the distal tail region have MSDs higher than those of water molecules
+  close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
+  compared to 1.2 nm$^2$ outside the distal tails. This anomaly is likely a 
+  consequence of lower density in the distal tails relative to the pores,
+  leading to faster diffusion in the tails (see Figure~\ref{S-fig:total_density}),
+  as well as slowed diffusion of water molecules in the pores via hydrogen bonds
+  with other water molecules and association with sodium ions. Water molecules 
+  are less likely to hydrogen bond with each other while in the distal tail 
+  region since they are interspersed between chains, while those in 
+  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
+  %MRS4: but there is also H-bonding to ions and carboxylate groups, which seems like they should be even stronger than water-water.
+  hydrogen bonding between water molecules near the pore center versus those in 
+  the distal tail region. Additionally, an average of 65\% of water molecules in
+  the pores of the 5 wt\% water system are associated with a sodium ion each frame
+  compared to 44 \% in the 10 wt\% water system. There is a negligible amount of
+  hydrogen bonds between water molecules and monomer head groups.
+
   In the 10 wt\% water system, water molecules that spend the majority of 
@@
   water molecules that spend $>$ 95\% of their time in the distal tail region, 
-  the MSD of distal tail water decreases 8-fold. 
+  the MSD of distal tail water decreases 8-fold from 59.6 to 8.2 nm$^2$. 
   %MRS4: did it really decrease? From what?  What was the previous definision.
 
-  % Changing pore radius does not change conclusion here.
-  In the 5 wt\% water system, water molecules that spend the majority of their 
-  time in the distal tail region have MSDs comparable to those of water molecules
-  close to the pore center. The MSD of distal tail water molecules is 1.71 nm$^2$.
-  %MRS4: might not be clear to the reader what the consequence of this MSD value is above, since it's not compared to anything.
-  %MRS4: interesting the water in the tails is almost as fast as the water in the 10% weight. 
-  This anomaly is likely a consequence of low density in the distal tails (see
-  Figure~\ref{S-fig:total_density}) as well as structuring of water molecules via
-  hydrogen bonding. 
-  %MRS4: a bit confusing, since H-bonding occurs in both 10 and 5?
-Water molecules are less likely to hydrogen bond while in the
-  distal tail region since they are interspersed between chains, while those in 
-  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
-  %MRS4: but there is also H-bonding to ions and carboxylate groups, which seems like they should be even stronger than water-water.
- hydrogen bonding between water molecules near the pore center versus those in 
-  the distal tail region. While a similar observation holds for the 10 wt\% system,
-  its high water content facilitates a less crowded environment where diffusion
-  of water molecules dominates.  
-  %MRS4: math seems a little inconsistent.  Does the tail water move the same rate in 5 and 10%? Seems like it should.
-  %MRS4: but above would tend to indicate that it moves 51/8 = 6.4 times faster in the tails in 10%? 
-  %MRS4: think about reading over/describiing the tail water here
-  %MRS4: would probably be useful to the reader to specify that we are neglecting transport in the tails here.
+  Because the MSD of water in the pores of the 10 wt\% system is significantly
+  higher than that in the tails, we restricted our studies of transport to 
+  solutes in the pore region. Transport of solutes in the pores will be the 
+  limiting factor that determines permeability and rejection. Although we showed
+  the opposite in the 5 wt\% water system, water transport is significantly slower
+  than in the 10 wt\% system. For practical applications, a membrane with water 
+  transport properties comparable to the 10 wt\% system is far more feasible than
+  the 5 wt\% system.
+
+%  45 \% of water molecules associated with sodium in 5 wt\% system
+%  
+%  While a similar observation holds for the 10 wt\% system,
+%  its high water content facilitates a less crowded environment where diffusion
+%  of water molecules dominates.  
+%  %MRS4: math seems a little inconsistent.  Does the tail water move the same rate in 5 and 10%? Seems like it should.
+%  %MRS4: but above would tend to indicate that it moves 51/8 = 6.4 times faster in the tails in 10%? 
+%  %MRS4: think about reading over/describiing the tail water here
+%  %MRS4: would probably be useful to the reader to specify that we are neglecting transport in the tails here.
+%
+%  Hydrogen bonds to charged things. Dipole-point charge stronger than dipole-dipole
+%  Quantify water 
+%
+%  10 wt will be the only practical membrane.
+%
+%  Set up simulations with high percent methanol
+
  \subsubsection{Transport of Small Polar Solutes}\label{section:general_transport_solutes}
@@
   are slowed by interactions between monomer functional groups and ions. 
-  %MRS4: sentence here seems like out of scope for the section title. 
-  Solutes
-  with hydrophobic character partition out of the pore and are slowed by densely
-  packed organic monomer components. 
-  %MRS4: this above seems like a general statement for all transport, not just small polar solutes?
-Should there be a bit of an introduction to transport as a whole before going into specific molecular classes?
-  A thorough understanding of these interactions
-  will help us to create monomer design principles. We will begin our analysis by
-  considering the collective trends observed across all systems and then focus on
-  subsets of similar molecules.
+  A thorough understanding of these interactions will help us to create monomer
+  design principles. We will begin our analysis by considering the collective
+  trends observed across all systems and then focus on subsets of similar molecules.
 
@@
   water system. Clearly the equilibrium water content of a given LLC system will 
-  determine its viability for real separations.  % BJC: last sentence too much speculation?
+  determine its viability for real separations.
 
@@
   against their MSD in Figures~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
-  Of all the solutes, %we believe 
-  methanol 
-  %MRS4:
-  %added
-  likely
-  is subject to the least hindrance by
-  the membrane due its small size. Therefore we fit Equation~\ref{eqn:stokes-einstein}
-  so that it intersects methanol's MSD. 
-  %MRS4: intersect where?  Might not be clear to readers that next sentence is a continuation of the process in the sentence above.
-  The uncorrected version of 
+  Of all the solutes, methanol likely is subject to the least hindrance by
+  the membrane due its small size. Therefore we fit Equation~\ref{eqn:msd-stokes-einstein}
+  so that it intersects with methanol's average MSD and radius. The uncorrected version of 
   Equation~\ref{eqn:stokes-einstein} ($f$=1) is plotted and converges to the same value as the
@@
   \end{subfigure}
-  %MRS4: suggest cutting off the density in height at 1.0, so that the scales of the other molecules can be seen.
-  %MRS4: below - specify which set this is.
-  \caption{(a) The MSDs of the solutes in this set descend in order of their size, except
+  \caption{(a) The MSDs of diols, triols and sugars descend in order of their size, except
   for propylene glycol which moves exceptionally slow. The MSD of ethylene glycol 
@@
   dimethyl formamide (Figure~\ref{fig:hop_lengths}). Acetone and 
-  tetrahydrofuran perform slightly larger hops but low hop frequencies
+  tetrahydrofuran perform slightly larger hops but with low hop frequencies
   (see Figure~\ref{fig:hopfreq}).
@@
   molecules in our model of the H\textsubscript{II} phase formed by the liquid 
-  crystal monomer Na-GA3C11.
+  crystal monomer Na-GA3C11. We found that transport of solutes is primarily
+  governed by water content as well as the chemical functionality of the solute
+  with respect to the chemical structure and functionality of the LLC monomer 
+  and ion present.
 
@@
   \end{enumerate}
+
+  The chemical functionality of solutes influences the degree to which
+  they are affected by each trapping mechanism. Simple alcohols tend to
+  partition into the tail region as their hydrophobic tail increases in length.
+  Alcohols and sugars with multiple hydroxyl groups are very stable
+  in the pore region, but frequent hydrogen bonds with monomer head 
+  groups prevents them from diffusing quickly. This effect is reduced when
+  hydroxyl groups are replaced with thiols but the solutes become less
+  stable in the pore. Finally, solutes with carbonyl groups, which includes
+  the ketones, amides and hydrogen bond acceptors, associate with
+  sodium ions, temporarily immobilizing them when the sodium ions are 
+  simulateneously partially bound to a monomer head group.
 
@@
   ion may offer some interesting behavior.
-  %MRS4: abrupt ending . . . think about a better way to wrap up that focuses on what was learned as well.
-  %BJC: future work? i.e. talk about mathematical modeling 
-  %MRS4: the modeling is scietifically a bit different.  MAybe nto
 
@@
 
+  The authors thank Christopher Calderon and Gregory Morrin for helping kick start
+  our studies of subdiffusive transport. Additionally, the authors thank 
+  Douglas Gin and Richard Noble for their guidance on past and present experimental
+  research on LLC membranes and for reading over this manuscript before submission.
+
   \clearpage

### 2019-04-30 Ben_Manuscripts/transport/figures/same_residue_rdf.py

@@ -11,7 +11,7 @@ r = 'BUT'
 atoms = ['C', 'O']
 wt=10
 
-opacity = 0.4
+opacity = 0.2
 
 fig, ax = plt.subplots()
 

### 2019-04-30 Ben_Manuscripts/transport/Draft.tex
Revisions after full read-through

@@
   pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
-  size, limiting selectivity.~\cite{werber_materials_2016}.
+  size, limiting their selectivity.~\cite{werber_materials_2016}.
 %  Therefore, multiple membrane passes may be necessary in order to achieve 
@@
   selectivity of RO membranes while maintaining the high permeability
-  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} LLC
+  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
   phase is formed when LLC monomers self-assemble into hexagonally packed
@@
   Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
-  We developed techniques for equilibrating the hexagonal phase formed by neat 
+  We developed techniques to simulate the hexagonal phase formed by neat 
   monomer as well as with varying amounts of water in the pores.
@@
   the hydrophilic head groups of the LLC monomers are colored orange with all else
-  colored gray. (a) Membrane pores are approximately straight and (b) are packed 
-  hexagonally.}\label{fig:membrane_rendering}
+  colored gray. We expect that transport will be primarily determined by solute
+  behavior within the pores. (a) Membrane pores are approximately straight and (b)
+  are packed hexagonally.}\label{fig:membrane_rendering}
   \end{figure}
@@
   character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
-  the membrane in which solutes are placed. 
-  We have listed the solutes studied along with the abbreviations that
+  the membrane in which we placed solutes. We have listed the solutes studied along with the abbreviations that
   we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
-  Note that, in order to avoid studying charge species, we have only studied
+  Note that, in order limit our studies to uncharged species, we have only studied
   %BJC: citations for pKa's
   acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
-  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
-  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
-  same time as protonated acetic acid. In any case, we are more interested 
-  in mechanisms of interaction with specific chemical functionality more than 
-  the behavior of specific molecules.
+  pKa of acetic acid is 4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} 
+  Assuming that the pKa of gallic acid is similar to NaGA3C11, it is possible
+  for our sodium salted monomer to exist at the same time as protonated acetic
+  acid. In any case, we are more interested in mechanisms of interaction with
+  specific chemical functionality more than the behavior of specific molecules.
 
@@
   \caption{Names of solutes along with their molecular structures and the
-  abbreviations which we use in this paper. Colors corresponds to solute groupings
-  and are used in many plots. Blue corresponds to simple alcohols, red to 
-  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
-  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.}\label{table:abbreviations}
+  abbreviations which we use in this paper. Colors correspond to solute groupings
+  and are used in many plots. 
+%  Blue corresponds to simple alcohols, red to 
+%  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
+%  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.
+  }\label{table:abbreviations}
   \end{table}
@@
 
-  We then present our efforts to understand how small molecules, 
-  including water, partition within the pores. From a macroscopic perspective,
-  it might make sense to hypothesize that the water and polar solutes spend
-  their time exclusively in the tube-like hydrophilic pore region. Our
+  We then present our efforts to understand how water partitions within the pores.
+  From a macroscopic perspective, it might make sense to hypothesize that water 
+  spends its time exclusively in the tube-like hydrophilic pore region. Our
   previous work showed that there is a gradual compositional transition from
@@
   necessarily stay confined to the centers of the pores or even within the 
-  pore region. We then study the gradient in composition of solutes and 
-  water and any resultant influence it might have on mechanistic properties.
+  pore region. We use this information in order to justify our restriction
+  of solute transport studies to just the pore region.
+
+%  We then study the gradient in composition of solutes and 
+%  water and any resultant influence it might have on mechanistic properties.
 
@@
   We investigate the differences in solute motion, specifically its mean 
-  squared displacement (MSD), based on a solute's size, shape and chemical
+  squared displacement (MSD), based on a solute's size and chemical
   functionality. We will study the interactions between solutes, the membrane,
@@
 
-  There are also a couple of questions that this study that are beyond the 
-  scope of this study. First, we will not study the concentration dependence of the observed transport
+  There are also a couple of questions that are beyond the scope of this study.
+  First, we will not study the concentration dependence of the observed transport
   rates. Although the average MSD might change with concentration, we are 
@@
   to understand the mechanistic details in various membrane regions; 
-  This work represents a starting point for observing the types of interactions
-  which occur between isolated solutes and the membrane.
+  this work represents a starting point for observing the types of interactions
+  that occur between isolated solutes and the membrane.
 
@@
   We ran all molecular dynamics simulations and energy minimizations using GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
+
+  \subsection{Solute Parameterization}\label{method:parameterization}
+
+  We parameterized the interaction potential for the monomer and solutes using 
+  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
+  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
+  We use GAFF as it has been used extensively for use with organic molecules.
+  We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
+  with QUACPAC from Openeye Scientific Software.
 
@@
   built our initial configurations with water in both regions, close to the expected
-  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
+  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
+  Information). We define the distal tail region to be ca. 1.5 nm from the pore
   center based on the minimum in the radial distribution of water
@@
   To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
-  center of each pore of the equilibrated cross-linked configuration. Our choice of 6
-  solutes per pore provided a balance of a useful amount of data for generating 
-  statistics and a low degree of interaction between solutes (see 
+  center of each pore of the equilibrated cross-linked configuration, for a total of 24
+  solutes. Our choice of 6 solutes per pore provides a balance of a useful amount of 
+  data for generating statistics and a low degree of interaction between solutes (see 
   Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
@@
 
-  \subsection{Solute Parameterization}\label{method:parameterization}
-
-  We parameterized the interaction potential for the monomer and solutes using 
-  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
-  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
-  We use GAFF as it has been used extensively for use with organic molecules.
-  We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
-  with QUACPAC from Openeye Scientific Software.
-
   \subsection{Mean Squared Displacement}\label{method:MSD}
 
-  We measured the time-averaged $z$-direction mean squared displacement (MSD) of the
-  centers of mass (COM) of each solute over the course of 1 $\mu$s MD simulations using 
+  We measured the time-averaged $z$-direction (parallel to the pores) mean squared
+  displacement (MSD) of the centers of mass (COM) of each solute over the course of 
+  1 $\mu$s MD simulations using 
   Equation~\ref{eqn:tamsd}:
@@
 
-  The $z$-direction MSD of water in the 10 wt\% system is linear. Therefore, for
+  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear. Therefore, for
   the purpose of comparison, we calculated its diffusion constant by fitting a line
@@
   we chose to use a simpler and more intuitive metric since we are only interested
-  in observing trends in the solute mean squared displacement as a function
+  in observing trends in the solute MSD as a function
   of solute size.
@@
   just the $z$-direction, in order to detect lateral hops. However,
-  hop lengths are reported as their displacement the $z$-direction.
+  hop lengths are reported as their displacement in the $z$-direction.
   We reported the standard error in the average hop lengths by 
@@
   hops per 1000 ns as the $\lambda$ parameter in a Poisson distribution.
-  We calculated the 1--$\sigma$ confidence intervals of the probability % BJC: not sure best way to write 1-sigma CI
+  We calculated the 1$\sigma$ confidence intervals of the probability % BJC: not sure best way to write 1-sigma CI
   distribution of hops per 1000 ns based on the corresponding Poisson 
@@
   show that our conclusions are insensitive to this definition within a 
-  reasonable range of distances and angles. We determined the average percentage
-  of solutes which actively participated in a hydrogen bond interaction with 
-  monomers each frame. We only counted unique solute--monomer hydrogen bond 
-  interactions, meaning solutes that hydrogen bond more than once simultaneously were classified as a
-  single pairing event. We determined the standard error of this calculation
-  by bootstrapping over each solute's trajectory. For each bootstrap trial,
-  we randomly chose 24 solutes with replacement and calculated the average
-  active solute-monomer hydrogen bonds per frame.
+  reasonable range of distances and angles.
+
+  We determined the average percentage of solutes
+  which actively participated in a hydrogen bond interaction with monomers 
+  each frame. Unless noted otherwise, we only counted unique solute--monomer
+  hydrogen bond interactions, meaning solutes that hydrogen bond more than 
+  once simultaneously were classified as a single pairing event. We determined
+  the standard error of this calculation by bootstrapping over each solute's 
+  trajectory. For each bootstrap trial, we randomly chose 24 solutes with 
+  replacement and calculated the average active solute--monomer hydrogen bonds per frame.
 
@@
   coordinated with water at an O--Na distance of between 2.3 and 2.5 \AA.
-  \cite{rowley_solvation_2012} We used 2.5 \AA~as the distance cut-off. We 
-  found that this approach is more useful than calculating the 3D spherical
-  radial distribution function because it gives detailed frame-by-frame 
-  information rather than an average.
-
-  Using our procedure we found that sodium ions in a solution of TIP3P water
+  \cite{rowley_solvation_2012} We used 2.5 \AA~as the distance cut-off in our
+  calculations. We found that this approach is more useful than calculating 
+  the 3D spherical radial distribution function because it gives detailed 
+  frame-by-frame information rather than an average.
+
+  Using our procedure, we found that sodium ions in a solution of TIP3P water
   coordinate with an average of 3.6 water molecules. We created a 4 x 4 x 4
@@
   a sodium ion each frame. Our calculation procedure is analogous to that for
-  solute-monomer hydrogen bond interactions outlined in the previous section.
+  solute--monomer hydrogen bond interactions outlined in the previous section.
 
@@
   Hydrogen bond lifetimes appear to be distributed according to a power law or an
-  exponential function. A number of researchers provide evidence that supports a 
+  exponential function (see Figure~\ref{S-fig:lifetime_distributions} of the 
+  Supporting Information). A number of researchers provide evidence that supports a 
   power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
@@
   Due to memory limitations, we could not collect data frequently enough to provide a
-  %MRS4: tweaking to 
   sufficient answer to this question so when comparing solutes, we use the 95\textsuperscript{th} 
@@
   normalized by the volume of the annulus defined by the bin edges.
-  We generated 1-$\sigma$ confidence intervals by bootstrapping the 
+  We generated 1$\sigma$ confidence intervals by bootstrapping the 
   RDFs of each individual solute 200 times. For each solute, we obtained
@@
   spaced in the $z$-direction, whose ($x$, $y$) coordinates are defined
-  based on the center of mass of all head groups closest, in $z$, to the
+  based on the COM of all head groups closest, in $z$, to the
   given point. When calculating RDFs, the radial distance from the pore 
-  center is based on the distance between the solute center-of-mass and
+  center is based on the distance between the solute COM and
   the linearly interpolated ($x$, $y$) coordinates of the pore center 
@@
   reference. The head group RDF shown is the average of the head group
-  RDFs for each solute system in the plot. We generated 1-$\sigma$ 
+  RDFs for each solute system in the plot. We generated 1$\sigma$ 
   confidence intervals by bootstrapping the RDFs in the same way we did
-  the solutes. We scaled the head group RDF so that it would be visible
+  the solutes. We scaled the head group RDF so that it would be in frame
   next to solute RDFs.
@@
 
-  Before beginning the analysis of solute transport behavior, it is important to
+  Before beginning our analysis of solute transport behavior, it is important to
   elucidate the topology of the membrane pores in solvated systems.
@@
   5 and 10 wt\% water systems. In dry systems, the pore center is densely 
-  filled with sodium ions and head groups. The peak head group density occurs
-  within 0.25 nm of the pore center. In hydrated systems, water occupies, 
+  filled with sodium ions and head groups. In hydrated systems, water occupies, 
   and is densest, at the center of each pore. The density of sodium ions is 
@@
   0.15 to 0.4 nm from the pore center. There is an appreciable density of head groups
-  crowding the pore center (b) In the 5 wt\% system, monomer head 
+  crowding the pore center. (b) In the 5 wt\% system, monomer head 
   groups retreat radially in order to make room for water molecules at the pore center.
@@
   region of both systems. 28\% and 31\% of the total water is present in the
-  tail regions of the 5 and 10 wt\% water systems respectively. See 
+  distal tail regions of the 5 and 10 wt\% water systems respectively. See 
   Section~\ref{S-section:water_content_equil} of the Supporting Information 
@@
   In the 10 wt\% water system, water moves about 51 times faster than sodium 
-  and in the 5 wt\% system, water moves about 49 times faster than sodium. Assuming
-  long timescale Brownian behavior of water in the 10 wt\% system, we measured its
-  diffusivity to be $7.45 \times 10^{-7}$cm$^2$ / s which is only 1.4\% that of bulk TIP3P 
+  and in the 5 wt\% system, water moves about 49 times faster than sodium. Due to
+  the linearity of water's MSD in the 10 wt\% water system, we assumed
+  long timescale Brownian behavior and measured its diffusivity to be 
+  $7.45 \times 10^{-7}$cm$^2$/s which is only 1.4\% that of bulk TIP3P 
   water.~\cite{mahoney_diffusion_2000} %BJC: 7.45e-07 versus 5.19e-05 cm^2/s
@@
   \end{subfigure}
-  \caption{(a) The MSD of water in the 10 wt\% water system is about 51 times
-  higher than water in the 5 wt\% water system. (b) The MSD of sodium in the
-  10 wt\% water system is about 49 times higher than sodium in the 5 wt\% 
-  water system.}\label{fig:msd_comparison}
+  \caption{(a) The $z$-direction MSD of water in the 10 wt\% water system 
+  is about 51 times higher than water in the 5 wt\% water system. Water 
+  appears to exhibit Brownian motion in the 10 wt\% system due to its
+  linear MSD. (b) The MSD of sodium in the 10 wt\% water system is about 
+  49 times higher than sodium in the 5 wt\% water system.}\label{fig:msd_comparison}
   \end{figure}
@@
   On average, sodium ions coordinate with 1 carboxylate group in the 10 wt\% water
-  system and 0.8 carboxylate groups in the 5 wt\% water system.
+  system and 0.8 carboxylate groups in the 5 wt\% water system. This behavior likely
+  slows their motion considerably.
   % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
   % since the averages were divided by 800 instead of 400
+
+  In the 10 wt\% water system, water molecules that spend the majority of 
+  their time in the distal tail region move significantly slower than those
+  close to the pore center. In Figure~\ref{fig:water_msd_comparison}, we 
+  constructed the MSD curves based on water molecules that spent $>$ 95\% of their
+  time outside the distal tail region. If we instead restrict our calculation to
+  water molecules that spend $>$ 95\% of their time \textit{in} the distal tail region, 
+  the MSD of distal tail water decreases 8-fold from 59.6 to 8.2 nm$^2$.
 
@@
   consequence of lower density in the distal tails relative to the pores,
-  leading to faster diffusion in the tails (see Figure~\ref{S-fig:total_density}),
+  leading to faster diffusion in the tails,
   as well as slowed diffusion of water molecules in the pores via hydrogen bonds
@@
 
-  In the 10 wt\% water system, water molecules that spend the majority of 
-  their time in the distal tail region move significantly slower than those
-  close to the pore center. In Figure~\ref{fig:water_msd_comparison}, we 
-  constructed the MSD curves based on water molecules that spent $>$ 95\% of their
-  time outside the distal tail region. If we instead restrict our calculation to
-  water molecules that spend $>$ 95\% of their time in the distal tail region, 
-  the MSD of distal tail water decreases 8-fold from 59.6 to 8.2 nm$^2$. 
-  %MRS4: did it really decrease? From what?  What was the previous definision.
-
   Because the MSD of water in the pores of the 10 wt\% system is significantly
-  higher than that in the tails, we restricted our studies of transport to 
-  solutes in the pore region. Transport of solutes in the pores will be the 
+  higher than that in the tails, we've restricted our studies of transport to 
+  solutes close to the pore center. Transport of solutes in the pores will be the 
   limiting factor that determines permeability and rejection. Although we showed
@@
   design principles. We will begin our analysis by considering the collective
-  trends observed across all systems and then focus on subsets of similar molecules.
+  trends observed across all systems and then focus on subsets of molecules
+  with structural similarities.
 
@@
   significantly larger in the 10 wt\% system than those in the 5 wt\% water 
-  system (Figure~\ref{fig:msds}). The fastest moving solute in both cases, 
+  system (see Figures~\ref{fig:all_msds_5wt} and~\ref{fig:all_msds_10wt}). The fastest moving solute in both cases, 
   methanol, has an MSD about 175 times larger in the 10 versus the 5 wt\%
@@
   against their MSD in Figures~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
-  Of all the solutes, methanol likely is subject to the least hindrance by
+  Of all the solutes, methanol is likely subject to the least hindrance by
   the membrane due its small size. Therefore we fit Equation~\ref{eqn:msd-stokes-einstein}
   so that it intersects with methanol's average MSD and radius. The uncorrected version of 
-  Equation~\ref{eqn:stokes-einstein} ($f$=1) is plotted and converges to the same value as the
+  Equation~\ref{eqn:msd-stokes-einstein} ($f$=1) is plotted and converges to the same value as the
   corrected form for large radii (see Section~\ref{method:stokes}). Although both curves are 
@@
   pore center and more frequent hops occur when solutes are close to the pore center.
-  (b) The time-averaged MSD of ethanol is sub-linear which suggests transport is
+  (b) The time-averaged MSD of ethanol is sublinear which suggests transport is
   governed by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
@@
   which are stabilized through electrostatic interactions with sodium ions. 
-  In Figure~\ref{fig:na_coordination}, we've plotted the percentage
-  of sodium ions coordinated to the oxygen atoms of each solute as well as the
-  95\textsuperscript{th} percentile of sodium association times. The degree and length of 
+  In Figure~\ref{fig:na_coordination}, we've plotted the average percentage
+  of solutes coordinated to a sodium ion each frame as well as the
+  95\textsuperscript{th} percentile of sodium association lifetimes. The degree and length of 
   coordination between solutes and sodium in the 5 wt\% water system is higher
@@
   drop in sodium ion association for solutes that do not contain carbonyl 
-  groups or multiple hydroxyl groups to compensate. The corresponding dwell
-  times follow a similar trend, however the dwell times of highly coordinated 
+  groups or multiple hydroxyl groups to compensate. The corresponding association
+  lifetimes follow a similar trend, however the association lifetimes of highly coordinated 
   solutes with multiple hydroxyl groups are generally lower since association
@@
   head groups. The radial distribution function of atoms located at opposite ends
-  of butanol shows that, on average, oxygen atoms are situated closer to the pore
-  centers than the most distal carbon atoms. This suggests that alcohols tend to 
-  orient themselves like the liquid crystal monomers, with hydrophilic components
+  of butanol (Figure~\ref{fig:butanol_CO}) shows that, on average, oxygen atoms are situated closer to the pore
+  centers than the most distal carbon atoms. This suggests that long chain alcohols
+  will tend to orient themselves like the liquid crystal monomers, with hydrophilic components
   directed towards the pore centers.
@@
   a given alcohol's preference towards hydrogen bonds with the carboxylate groups
-  of ether linkages increases with increasing hydrophobic character. (d) The average location of 
+  over ether linkages increases with increasing hydrophobic character. (d) The average location of 
   butanol's oxygen atom is closer to the pore center than its most distal carbon
@@
 
-  The order of the MSDs of solutes in this grouping are roughly consistent with 
+  The order of the MSDs of the diols, triols and sugars are roughly consistent with 
   their size; however, propylene glycol moves exceptionally slowly (see 
@@
   hydroxyl groups cause solutes to favor the water-rich pore region where there 
-  is the least hindrance to movement (See Figure~\ref{fig:polyols_rdf}). Tetrose,
+  is the least hindrance to movement (see Figure~\ref{fig:polyols_rdf}). Tetrose,
   ribose and glycerol are densest close to the pore center. They spend a greater
@@
   \end{subfigure}
-  \caption{(a) The MSD of the solutes decreases and the deviation from
+  \caption{(a) The MSD of ketones and amides decreases and the deviation from
   Stokes-Einstein predicted behavior increases with molecular size.
@@
   solute MSD. Peaks in the RDFs of urea, acetamide and acetone that appear 
-  0.2 - 0.4 nm from the pore center are 
-  %MRS4: seems like we could make it stronger with ``likely do''?
-  likely due to coordination with sodium
+  0.2 - 0.4 nm from the pore center are likely due to coordination with sodium
   ions. (c) The amides hydrogen bond with water far less than acetic acid, 
@@
   \includegraphics[width=\textwidth]{msd_radius_sulfur_10wt.pdf}
-  \caption{}\label{fig:SOH_GCL_comparison}
+  \caption{}\label{fig:msd_radius_sulfur_10wt}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{thiol_comparison_DMS.pdf}
-  \caption{}\label{fig:DMP_GLY_comparison}
+  \caption{}\label{fig:DMS_ATO_comparison}
   \end{subfigure}
@@
 
-  Mercaptoethanol has a similar average MSD and RDF to ethylene glycol.
+  Mercaptoethanol has a similar average MSD and RDF to ethylene glycol
+  (see Figures~\ref{fig:all_msds_10wt} and~\ref{fig:SOH_GCL_comparison}).
   There is a much larger uncertainty associated with mercaptoethanol's
@@
   2,3-dimercapto-1-propanol exhibits slower transport than glycerol 
-  because more of it partitions into the tail region. 2,3-dimercapto-1-propanol
+  because more of it partitions into the tail region (see 
+  Figure~\ref{fig:DMP_GLY_comparison}). 2,3-dimercapto-1-propanol
   spends 27\% less time in the pore region than glycerol. 
@@
 
-  DMSO has a comparable MSD to acetone even though it is a larger molecule. 
-  DMSO spends 17\% more time in the pore than acetone. 
+  DMSO has a comparable MSD to acetone even though it is a larger molecule
+  (see Figure~\ref{fig:msds}). DMSO spends 17\% more time in the pore than acetone. 
 %  The density of DMSO is higher than acetone in the pore region, except for
@@
 
-  \subsection{Hydrogen Bond Acceptors}  % Need a better heading since all molecules in this study are acceptors
+  \subsection{Solutes Unable to Donate Hydrogen Bonds}  % Need a better heading since all molecules in this study are acceptors
 
@@
   Association between sodium and solutes in this set are also among the longest,
-  only beat by other solutes with carbonyl groups and ribose.
+  only beaten by other solutes with carbonyl groups and ribose.
 
@@
   \begin{enumerate}
-    \item A solute can become stuck among monomer tails. 
-    \item A solute can donate hydrogen bonds to immobile monomers.
-    \item A solute can associate with a bound counterion.
+    \item Solutes can become entangled among monomer tails. 
+    \item Solutes can donate hydrogen bonds to immobile monomers.
+    \item Solutes can associate with counterions.
   \end{enumerate}
@@
   groups prevents them from diffusing quickly. This effect is reduced when
-  hydroxyl groups are replaced with thiols but the solutes become less
+  hydroxyl groups are replaced with thiol groups but the solutes become less
   stable in the pore. Finally, solutes with carbonyl groups, which includes
-  the ketones, amides and hydrogen bond acceptors, associate with
-  sodium ions, temporarily immobilizing them when the sodium ions are 
-  simulateneously partially bound to a monomer head group.
+  the ketones, amides and solutes that can only accept hydrogen bonds, associate
+  with sodium ions, temporarily slowing or immobilizing them.
 
@@
 
-  \section{Supporting Information}
+  Combined with our previous structural work, it is relatively straightforward
+  to apply our approaches to the screening of solute interactions with new 
+  H\textsubscript{II} phase-forming monomers.
+
+  \section*{Supporting Information}
 
@@
 
-  \section{Acknowledgements}
+  \section*{Acknowledgements}
 
@@
   Engineering Discovery Environment (XSEDE), which is supported by National
-  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
+  Science Foundation (NSF) grant number ACI-1548562. Specifically, it used the Bridges
   system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
   Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
-  which is supported by the National Science Foundation (awards ACI-1532235 and
+  which is supported by the NSF (awards ACI-1532235 and
   ACI-1532236), the University of Colorado Boulder, and Colorado State
@@
 
-  \section{TOC Graphic}
+  \section*{TOC Graphic}
 

### 2019-04-30 Ben_Manuscripts/transport/Supporting_Information.tex
Revisions after full read-through

@@
 
-\title{Supporting Information: The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Supporting Information: Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
 
-  \texttt{/setup/param.sh} & TBD & Parameterize liquid crystal monomers and 
-  solutes with GAFF \\ \hline
+  \texttt{/setup/param.sh} & 2.1 & Parameterize liquid 
+  crystal monomers and solutes with GAFF \\ \hline
 
-  \texttt{/setup/solvation\_equilibration.py} & TBD & Add water to the pores and tails
+  \texttt{/setup/solvation\_equilibration.py} & 2.2 & Add water to the pores and tails
   in order to achieve a specific total water content and ratio of water molecules in each
@@
 
-  \texttt{/setup/input.py} & TBD & Create GROMACS topology and .mdp files \\ \hline
+  \texttt{/setup/input.py} & 2.2 & Create GROMACS topology and .mdp files \\ \hline
 
-  \texttt{/setup/xlink.py} & TBD & Iteratively cross-link a configuration \\ \hline
+  \texttt{/setup/xlink.py} & 2.2 & Iteratively cross-link a configuration \\ \hline
 
-  \texttt{/setup/place\_solutes\_pores.py} & TBD & Place a desired number of solutes
+  \texttt{/setup/place\_solutes\_pores.py} & 2.2 & Place a desired number of solutes
   in the pore center, equally space in the $z$-direction. \\ \hline
 
-  \texttt{/analysis/msd.py} & TBD & Calculate the mean squared displacement of residues \\ \hline
+  \texttt{/analysis/msd.py} & 2.3 & Calculate the mean squared displacement of residues \\ \hline
 
-  \texttt{/analysis/rdf.py} & TBD & Calculate the cylindrical radial distribution function of
+  \texttt{/analysis/radius.py} & 2.4 & Calculate the maximum end-to-end distance of a solute over a trajectory \\ \hline
+
+  \texttt{/timeseries/forecast\_ctrw.py} & 2.6 & Construct dwell time and hop length distributions \\ \hline
+
+  \texttt{/analysis/rdf.py} & 2.7, 2.11 & Calculate the cylindrical radial distribution function of
   a solute or membrane component with respect to the pore centers. \\ \hline
 
-  \texttt{/analysis/hbonds.py} & TBD & Identify hydrogen bonds based on geometric criteria \\ \hline
+  \texttt{/analysis/hbonds.py} & 2.8 & Identify hydrogen bonds based on geometric criteria \\ \hline
 
-  \texttt{/timeseries/forecast\_ctrw.py} & TBD & Construct dwell time and hop length distributions \\ \hline
-
-  \texttt{/analysis/coordination\_number.py} & TBD & Calculate number of molecules or atoms within a
+  \texttt{/analysis/coordination\_number.py} & 2.9 & Calculate number of molecules or atoms within a
   cutoff distance of another type of molecule or atom. \\ \hline
 
-  \texttt{/analysis/ztrace.py} & TBD & Plot the center of mass $z$-coordinate of an atom or molecule
+  \texttt{/analysis/lifetime.py} & 2.10 & Calculate association lifetimes \\ \hline
+
+  \texttt{/analysis/ztrace.py} & 3.2.2 & Plot the center of mass $z$-coordinate of an atom or molecule
   versus time which is colored according to its distance from the pore center. \\ \hline
@@
   molecules to naturally penetrate the membrane from a water bath separating
-  periodic images of the system in the $z$-direction (See Figure~\ref{fig:gap}).
+  periodic images of the system in the $z$-direction (see Figure~\ref{fig:gap}).
   We allowed a dry, previously equilibrated system to further equilibrate in
@@
   times more water molecules occupy the tail region after 1000 ns of
-  equilibration (See Figure~\ref{fig:equilibrated_water_penetration}). Although
+  equilibration (see Figure~\ref{fig:equilibrated_water_penetration}). Although
   the water level in the pore appears to plateau in this system, it is clear that
   equilibration of this system is kinetically limited since water does not fill
-  the pores uniformly. The density of water along the pore axis, averaged over
-  the last 50 nanoseconds of simulation, is close to zero at the membrane center.
-  Therefore, we required a different equilibration technique in order to overcome
-  the kinetic limitation.
+  the pores uniformly (see Figure~\ref{fig:penetration_density}). The density of
+  water along the pore axis, averaged over the last 50 nanoseconds of simulation,
+  is close to zero at the membrane center. Therefore, we required a different
+  equilibration technique in order to overcome the kinetic limitation.
 
@@
   \end{subfigure}  
-  \caption{(a) Using an equilibrated dry configuration, we inserted a layer of water between
-           periodic copies of the system in the $z$-direction. (b) Water slowly enters 
-	   the membrane. Most water enters the tail region where the density of monomers is
-	   lowest. Water entering the pore plateaus after 500 ns. (c) Although the water
+  \caption{(a) Using an equilibrated dry configuration, we inserted a 3 nm thick layer 
+  of water between periodic copies of the system in the $z$-direction. (b) Water slowly
+  enters the membrane. Most water enters the tail region where the density of monomers
+  is lowest. Water entering the pore plateaus after 500 ns. (c) Although the water
   content of the pore appears equilibrated in (b), the density of water throughout
@@
   the pores with water by running \texttt{gmx solvate} on our initial
-  configuration and removing any water molecules placed outside of the pore
-  region. The GROMACS command \texttt{gmx solvate} places water molecules in
-  proximity to other atoms based on their van der waals radii and therefore does
+  configuration and removing any water molecules placed in the tail region. The
+  GROMACS command \texttt{gmx solvate} places water molecules in proximity to
+  other atoms based on their van der waals radii and therefore does
   a decent job of preventing equilibration issues. This also means that the
@@
 
+  \clearpage
+
   \section{Solute Interaction}\label{section:solute_interaction}
@@
   % BJC: not sure what the appropriate cut-off should be
-  where the center of a given solute came within 3.5 \AA of another same-solute
+  where the center of a given solute came within 3.5 \AA~of another same-solute
   center of mass.
@@
 %  \end{figure}
-
+  \clearpage
   \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}
@@
 
+  \clearpage
   \section{Pore Region Definition}\label{section:pore-region}
@@
   edge of the pore region in increments of 0.05 from 0.3 to 0.7. We
-  varied the cut-off in increments of 0.1 from 0.7 to 0.8 in order to
+  varied the cut-off in increments of 0.01 from 0.7 to 0.8 in order to
   increase our resolution about the maximum (see Figure~\ref{fig:pore_cutoff}). 
@@
   in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
-  increments of 0.1 from 0.7 to 0.8 in order to increase our resolution
+  increments of 0.01 from 0.7 to 0.8 in order to increase our resolution
   about the maximum.}\label{fig:pore_cutoff}
@@
 
+  \clearpage
+  \section{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}
+
+  In Section 2.8 of the main text, we established geometric criteria for the 
+  identification of hydrogen bond interactions. Namely, if the distance between the donor,
+  D, and acceptor, A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less
+  than 30\degree, then we consider the interaction to be a consequence of hydrogen bonding.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[trim={0 0.5cm 0.5cm 0.5cm}, clip, width=0.5\textwidth]{hbond_sensitivity_legend.pdf}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{hbond_sensitivity.pdf}
+  \end{subfigure}
+  \caption{We tested the sensitivity of our hydrogen bond detection to the chosen 
+  geometric criteria for hydrogen bonding. We varied the distance cut-off between 3.0 and
+  4.0 \AA, and varied the angle cut-off between 25 and 35 \degree.}\label{fig:hbond_sensitivity}
+  \end{figure}
+
+  We tested the sensitivity of this criteria to ensure that our conclusions
+  were not a strong function of the chosen criteria. In Figure~\ref{fig:hbond_sensitivity} we
+  plotted the results of the same calculation performed to create Figure~\ref{M-fig:multi_hbonds}c
+  of the main text. We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
+  angle cut-off between 25 and 35 \degree.
+
+  As the distance and angle cut-offs are increased, there is a slight increase in the total
+  number of hydrogen bonds, which is primarily manifested by an increased number of multiple-hydrogen-bond
+  interactions. Using our most lenient set of criteria (d = 4.0 \AA~and $\theta$ = 35 $\degree$), glycerol,
+  tetrose and ribose all show instances where they simultaneously hydrogen bond with 4 head group atoms.
+  In the strictest case (d = 3.0 \AA~and $\theta$ = 25 \degree), ribose is the only solute with a 
+  detected instance of a quadruple hydrogen bond.
+
+  We can draw the same conclusions from any of the plots in Figure~\ref{fig:hbond_sensitivity}:
+  \begin{enumerate}
+    \item An increased number of hydroxyl groups results in an increased number of hydrogen bond
+    interactions.
+    \item The number of multiple-hydrogen-bond interactions increases.
+    \item On average, propylene glcyol participates in more hydrogen bond interactions than 
+    ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)
+  \end{enumerate}
+
+  \section{Lifetime Distributions}\label{section:lifetime_distributions}
+
+  The distribution of hydrogen bond lifetimes and association lifetimes
+  for all solutes appears to be power law or exponentially distributed. 
+  Example distributions generated from ethylene glycol are shown in
+  Figure~\ref{fig:lifetime_distributions}.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{gcl_hbond_dist.png}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{gcl_coord_dist.png}
+  \caption{}
+  \end{subfigure}
+  \caption{The distribution of hydrogen bond lifetimes and association lifetimes of
+  ethylene glycol both appear to be power law or exponentially distributed. We
+  do not attempt to distinguish between the type of distribution and instead report
+  the 95\% confidence interval of association lifetimes.}\label{fig:lifetime_distributions}
+  \end{figure}
+
+  \clearpage
   \section{Pore Splines}\label{section:splines}
@@
   ratio $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is 
-  the length of the unit cell in the $z$-direction.
+  the length of the unit cell in the $z$-direction. The average tortuosity
+  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt\%
+  water systems respectively.
 
-  \section{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}
-
-  In Section~\ref{M-method:hbonds} of the main text, we established geometric criteria for the 
-  identification of hydrogen bond interactions. Namely, if the distance between the donor,
-  D, and acceptor, A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less
-  than 30\degree, then we consider the interaction to be a consequence of hydrogen bonding.
-
-  We tested the sensitivity of this criteria to ensure that our conclusions
-  were not a strong function of the chosen criteria. In Figure~\ref{fig:hbond_sensitivity} we
-  plotted the results of the same calculation performed to create Figure~\ref{M-fig:multi_hbonds}
-  of the main text. We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
-  angle cut-off between 25 and 35 \degree.
-
-  As the distance and angle cut-offs are increased, there is a slight increase in the total
-  number of hydrogen bonds, which is primarily manifested by an increased number of multiple-hydrogen-bond
-  interactions. Using our most lenient set of criteria (d = 4.0 \AA~and $\theta$ = 35 $\degree$), glycerol,
-  tetrose and ribose all show instances where they simultaneously hydrogen bond with 4 head group atoms.
-  In the strictest case (d = 3.0 \AA~and $\theta$ = 25 \degree), ribose is the only solute with a 
-  detected instance of a quadruple hydrogen bond.
-
-  We can draw the same conclusions from any of the plots in Figure~\ref{fig:hbond_sensitivity}. 
-  \begin{enumerate}
-    \item An increased number of hydroxyl groups results in an increased number of hydrogen bond
-    interactions.
-    \item The number of multiple-hydrogen-bond interactions increases.
-    \item On average, propylene glcyol participates in more hydrogen bond interactions than 
-    ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)
-  \end{enumerate}
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{\textwidth}
-  \centering
-  \includegraphics[trim={0 0.5cm 0.5cm 0.5cm}, clip, width=0.5\textwidth]{hbond_sensitivity_legend.pdf}
-  \end{subfigure}
-  \begin{subfigure}{\textwidth}
-  \includegraphics[width=\textwidth]{hbond_sensitivity.pdf}
-  \end{subfigure}
-  \caption{We tested the sensitivity of our hydrogen bond detection to the chosen 
-  geometric criteria for hydrogen bonding. We varied the distance cut-off between 3.0 and
-  4.0 \AA, and varied the angle cut-off between 25 and 35 \degree.}\label{fig:hbond_sensitivity}
-  \end{figure}
-
+  \clearpage
   \section{Total Membrane Density}\label{section:total_density}
@@
 
-  \section{Solute Pairing with Sodium}
-
-  \begin{figure}[!htb]
-  \centering
-  %MRS2: would be better if this was paired with ensemble data, instead of just one trajectory.
-  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
-  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
-  the majority of the trapping occurence between 400 and 600 ns. Regions
-  highlighted red or blue indicate times when methanol's oxygen atom is within 
-  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
-  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
-  \end{figure}
-
-  %BJC: could probably safely remove this figure
-  \section{Mercaptoethanol's range of behavior}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{SOH_trace.pdf}
-  \caption{}\label{fig:SOH_trace}
-  \end{subfigure}
-  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
-  to lengthy trapping. Large hops generally occur near the pore center while 
-  long entrapments occur while tangled among the monomer tails.}
-  \end{figure}
-
-  \section{THF-sodium Complexation}
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
-  \caption{Coordination of THF with sodium ions may help stabilize it inside the
-  pore region. For the first 700 ns of the trajectories shown, the center of mass
-  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
-  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
-  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
-  After 700 ns, THF separates from the sodium ion and moves closer to the head group
-  region.}\label{fig:thf_sodium_coordination}
-  \end{figure}
+%  \clearpage
+%  \section{Solute Pairing with Sodium}
+%
+%  \begin{figure}[!htb]
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
+%  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
+%  the majority of the trapping occurence between 400 and 600 ns. Regions
+%  highlighted red or blue indicate times when methanol's oxygen atom is within 
+%  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
+%  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
+%  \end{figure}
+%  
+%  \section{Mercaptoethanol's range of behavior}
+%  
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{SOH_trace.pdf}
+%  \caption{}\label{fig:SOH_trace}
+%  \end{subfigure}
+%  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
+%  to lengthy trapping. Large hops generally occur near the pore center while 
+%  long entrapments occur while tangled among the monomer tails.}
+%  \end{figure}
+%  
+%  \section{THF-sodium Complexation}
+%  
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
+%  \caption{Coordination of THF with sodium ions may help stabilize it inside the
+%  pore region. For the first 700 ns of the trajectories shown, the center of mass
+%  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
+%  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
+%  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
+%  After 700 ns, THF separates from the sodium ion and moves closer to the head group
+%  region.}\label{fig:thf_sodium_coordination}
+%  \end{figure}
   %MRS2: Can we show something that describes a distribution of multiple THF? this is just one, 
@@
 
-  \clearpage
-  \bibliography{transport}
+%  \clearpage
+%  \bibliography{transport}
 

### 2019-04-30 Ben_Manuscripts/transport/cover_letter.tex
Cover letter for J. Phys. Chem. B.

--- 2018-10-05 Ben_Manuscripts/structure_paper/cover_letter.tex
@@
 	\noindent Department of Chemical and Biological Engineering \hfill t 303-735-7860~~~~~~~~~~~~~~~~~~ \\
-	\noindent 596 UCB \hfill f 303-735-7860~~~~~~~~~~~~~~~~~~ \\
+	\noindent 596 UCB \hfill f 303-492-8425~~~~~~~~~~~~~~~~~~ \\
 	\noindent Boulder, Colorado 80309 \hfill michael.shirts@colorado.edu \\
@@
 
-	\noindent October 1st, 2018\\
+	\noindent May 3\textsuperscript{rd}, 2019\\
 
@@
 
-	We are submitting ``Understanding the Nanoscale Structure of Inverted Hexagonal 
-	Phase Lyotropic Liquid Crystal Polymer Membranes'' by Benjamin J. Coscia, Joseph
-	Yelk, Matthew A. Glaser, Douglas L. Gin, Xunda Feng, and Michael R. Shirts, for
+	\newcommand{\ManuscriptTitle}{Chemically Selective Transport in a Cross-linked 
+	H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+
+	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael R. Shirts, for
 	consideration for publication as an Article in the Journal of Physical Chemistry
@@
 
-	This article examines the atomistic structure of an inverted hexagonal phase 
-	self-assembled lyotropic liquid crystal (LLC) polymer membrane. To create these
-	materials, liquid crystal (LC) monomers self-assemble into ordered, uniform-sized
-	and hexagonally-packed nanopores. The nm-sized pore centers are charged and hydrophilic 
-	in nature which makes this type of membrane useful for highly selective aqueous 
-	separations of small solutes. By tuning the shape, size and chemical functionality
-	of LC monomers, one could intelligently design the pore environment. However, our 
-	current understanding of the nanoscopic pore structure is not yet adequate for us to
-	be able to controllably design membranes for solute-specific separations.
+	In this article, we use molecular dynamics (MD) simulations in order to observe 
+	transport of small solutes in an inverted hexagonal (H\textsubscript{II}) phase 
+	self-assembled lytropic liquid crystal (LLC) polymer membrane. Recently, we 
+	published our first article on this subject in which we built and characterized
+	an atomistic molecular model of an LLC membrane that is maximally consistent with experimental
+	observations. By observing transport of solutes within a similar model, we can 
+	learn the optimal ways to tune the shape, size and chemical functionality
+	of LC monomers in order to intelligently design the pore environment and facilitate
+	solute-specific separations.
 
-	In this paper, we used molecular dynamics (MD) simulations to model an
-	experimentally characterized LLC polymer membrane and learn about its detailed
-	atomistic structure. We simulated XRD patterns from the MD simulation trajectories
-	for comparison to experimental 2D wide-angle X-ray scattering (WAXS) and 1D 
-	small-angle X-ray scattering patterns. We found that 5 columns of stacked LLC 
-	monomers are likely to pack around the hydrophilic core of each pore. These 
-	columns likely move independently of each other	over time scales that we can not
-	simulate. Some of the structure previously attributed to monomer tail tilt is 
-	likely instead due to ordered tail packing. Although the system studied	has been
-	reported as ``dry'', small amounts of water appear necessary to fully reproduce 
-	all features from the experimental 2D-WAXS pattern due to asymmetries introduced 
-	by hydrogen bonds between the LLC monomer head groups and water molecules. 
-	Finally, we explored the composition and structure of the nanopores, showing there is 
-	composition gradient rather than an abrupt partition between the hydrophilic and
-	hydrophobic regions. The clearer picture of the nanoscopic structure
-	of these membranes provided in this study will enable a better understanding of the
-	mechanisms of small molecule transport within these nanopores. \\
+	In this work, we observe and quantify transport of water, sodium and 20 small
+	polar solutes within the pores of our atomistic H\textsubscript{II} phase LLC membrane
+	model. In general, all solutes exhibit subdiffusive transport behavior
+	characterized by intermittent hops between long periods of entrapment. However, 
+	due the pores' inhomogeneous architecture, we observed 3 different mechanisms
+	of entrapment. First, solutes can diffuse out of the pores and become entangled 
+	between tails. Second, many of the solutes are capable of donating hydrogen bonds
+	to monomer head groups for extended periods of time. Finally, solutes can associate
+	with monomer head group counter-ions within nanopores. Each solute is influenced 
+	by each mechanism to varying degrees dependent on its size and chemical 
+	functionality. We begin our discussion with a broad description of these mechanisms
+	in the context of all solutes before restricting the discussion to more detailed 
+	analyses of subsets of chemically-similar solutes.
 
@@
 	\noindent Benjamin J. Coscia \\
-    \noindent Joseph Yelk \\
-    \noindent Matthew A. Glaser
-    \noindent Douglas L. Gin \\
-    \noindent Xunda Feng \\
 

### 2019-05-01 Ben_Manuscripts/transport/Draft.tex
Updated TOC image
Finalized TOC image
Addressing Doug's comments on conclusions

@@
   We learned that the MSD of solutes, water and counter ions are highly 
-  dependent on LLC membrane water content. The MSD of these components is about
-  2 orders of magnitude larger in the 10 wt\% system than in the 5 wt\% system.
-  As more water is added to the system, the pores become less crowded with monomer
-  components. The amount of water in the pores deserves special attention when 
-  screening new monomers.
-
-  We observed three mechanisms of solute entrapment.
+  dependent on LLC membrane water content. As more water is added to the system, 
+  the pores become less crowded with monomer components. The MSDs of water and
+  sodium ions are nearly 2 orders of magnitude larger in the 10 wt\% system 
+  than in the 5 wt\% system. The amount of water in the pores deserves special
+  attention when screening new monomers.
+
+  The transport of polar solutes in this system is significantly slower than
+  that of water due to their interaction with the LLC monomers. We observed 
+  three primary mechanisms of solute entrapment within the pores.
   \begin{enumerate}
@@
   in the pore region, but frequent hydrogen bonds with monomer head 
-  groups prevents them from diffusing quickly. This effect is reduced when
-  hydroxyl groups are replaced with thiol groups but the solutes become less
+  groups prevent them from diffusing quickly. This effect is reduced when
+  hydroxyl groups are replaced with thiol groups, but the solutes become less
   stable in the pore. Finally, solutes with carbonyl groups, which includes
@@
   coordinate with counterions. Changing the size and valence of the counter 
-  ion may offer some interesting behavior.
-
-  Combined with our previous structural work, it is relatively straightforward
-  to apply our approaches to the screening of solute interactions with new 
-  H\textsubscript{II} phase-forming monomers.
+  ion may offer some interesting behavior. These hypotheses remain to be 
+  tested in future simulations of new monomers.
+
+  The optimal design of new LLC membranes for a given separation is not obvious.
+  Experimental progress up to this point in time is the culmination of an iterative 
+  educated guess-and-check framework. An array of solute-membrane interactions
+  ensuing from the chemically complex and inhomogeneous LLC membrane structure
+  as well as the complexity of the solutes themselves, have hindered the 
+  establishment of firm design criteria. Our atomistic modeling approach gives
+  us the opportunity to approximate these interactions at the molecular scale
+  so that we can observe them and think more critically about LLC membrane design. 
+%  We can use insights gained from our model to hypothesize and screen new monomers
+%  in order to rapidly increase LLC membrane development.
 
@@
 
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=3.25in]{toc_transport.pdf}
+  \end{figure}
+
 \end{document}

### 2019-05-06 Ben_Manuscripts/transport/Draft.tex
updated draft.

@@
   membrane's inhomogeneous composition gives rise to radially dependent
-  transport mechanisms with respect to the pore centers. In general, we 
-  observed that all solutes perform intermittent hops between lengthy
+  transport mechanisms with respect to the pore centers. 
+  %MRS3: remove qualifier?
+  %In general, 
+  We 
+  %MRS3: tense
+  %observed 
+  observe
+  that all solutes perform intermittent hops between lengthy
   periods of entrapment. Three different trapping mechanisms are 
@@
   All of these separations are possible in part with current commercial
-  membrane separation techniques but suffer from serious drawbacks. Currently,
+  membrane separation techniques, but
+  %MRS3: tweaking
+  all still
+  suffer from serious drawbacks. Currently,
   reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
@@
   material.~\cite{fritzmann_state---art_2007} Although they can perform highly
-  selective separations, high feed pressures, and thus large amounts of energy,
+  selective separations, high feed pressures and thus large amounts of energy
   are necessary in order to generate a useful permeate
@@
   membranes. Dischinger et al. studied a similar membrane and found that they do
-  not separate purely on the basis of size. Empirical modeling revealed correlations
+  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
   between various solute physicochemical properties and observed solute rejection. 
   Although there was some agreement with their empirical model, it does not
-  offer a sufficiently detailed explanation of governing molecular interactions.
-  ~\cite{dischinger_effect_2017}
+  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
 
@@
 %  %separation BY size exclusion; maybe rephrase?
-%  %BJC4: Hmm, by characerization, I mean testing their ability to separate, so I'm 
+%  %BJC4: Hmm, by characterization, I mean testing their ability to separate, so I'm 
 %  While size-exclusion is a useful separation, it 
@@
 %  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
-  %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
+  %MRS4: expand the above.  What was discovered, and why was it unfortunate to the thesis?  
   % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
@@
   \end{subfigure}
+  %MRS3: include a bit more description in the caption of what the system: This is the figure that provides the orientation to the readers of what they will be thinking about for the rest of the paper.
   \caption{In both figures, water molecules that occupy the pores are colored blue,
   the hydrophilic head groups of the LLC monomers are colored orange with all else
-  colored gray. We expect that transport will be primarily determined by solute
-  behavior within the pores. (a) Membrane pores are approximately straight and (b)
+  colored gray. 
+  %MRS3: probably this point below can be better addressed in the text; looks a little out of place here.
+  We expect that transport will be primarily determined by solute
+  behavior within the pores. 
+  (a) Membrane pores are approximately straight and (b)
   are packed hexagonally.}\label{fig:membrane_rendering}
@@
 
+  %MRS3: maybe say ``we present studies of''? ``This work'' is the paper, so using past tense is weird.
   In this work, we have studied the transport mechanisms exhibited by 20 
@@
   %the paper is completely written, later sections are not being written in the future. 
-  %MRS2: descriptions of experiements can be in the past.
-
+  %MRS2: descriptions of experiments can be in the past.   
+  %MRS2: look over this section at the end of the intro again for clarity - some paragraphs are too short (ideas introduced and brushed past quickly) sometimes without strong theses.
   We first address the structure of the pores formed in the membrane.
@@
   necessarily stay confined to the centers of the pores or even within the 
-  pore region. We use this information in order to justify our restriction
+  pore region. 
+  %MRS2: ``this information'' is ambiguous. Which information? Also, I'm not sure the paragraph above is enough to 
+  %demonstrate why we can/should neglect the tails.
+  We use this information in order to justify our restriction
   of solute transport studies to just the pore region.
@@
   and explanations of the observed transport mechanisms exhibited by water
-  and solutes. Given that the pores will restrict motion of the solutes, we
+  and solutes. 
+  %MRS2: The thesis of this paragraph could be stronger.
+expand ``pores will restrict motion of the solutes'' a little using the physical details about the pores; paint the picture that will be filled in with detail
+Given that the pores will restrict motion of the solutes, we
   anticipate that transport will be hindered in some way.
 
+  %MRS2: be consistent on tense.  What is presented in the paper is present tense.  We already studied it, we are presenting it.  
   We investigate the differences in solute motion, specifically its mean 
@@
 
-  There are also a couple of questions that are beyond the scope of this study.
+  There are also 
+  %a couple of questions that are beyond
+  several questions beyond
+  the scope of this study.
   First, we will not study the concentration dependence of the observed transport
@@
   of solutes in the pores, which could give us a better understanding of 
-  equilibrium solute partitioning. However, this information is not needed
-  to understand the mechanistic details in various membrane regions; 
-  this work represents a starting point for observing the types of interactions
+  equilibrium solute partitioning. However, this information is 
+  %MRS3: added - there might be mechanisms that only happen with multiple solutes in contact
+  likely
+  not needed
+  to understand the 
+  %MRS3: added
+  principal
+  mechanistic details in various membrane regions. 
+  %MRS3: broke sentence
+  This work 
+  %MRS3: added for flow
+  instead
+  represents a starting point for observing the types of interactions
   that occur between isolated solutes and the membrane.
@@
   Python scripts used to set up systems and conduct post-simulation trajectory 
-  analysis are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. 
+  analysis 
+  %MRS2: added to make sure it's clear the basic description is not JUST in the scripts.
+  (as described below and in the supporting information) are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. 
   %BJC: also link to readthedocs? I have the link in the repo 
+  %MRS2: either is fine. 
   The appropriate scripts to use for the subsequent calculations are summarized in 
   Table~\ref{S-table:python_scripts} of the Supporting Information.
-
   We ran all molecular dynamics simulations and energy minimizations using GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
@@
   may or may not be experimentally consistent but it is necessary for our results to be 
-  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
+  thermodynamically consistent;
+  %MRS3: providing some context
+  otherwise, water would slowly leak from the pore into the tail region over several hundred nanoseconds.
+We iteratively adjusted the pore radius in our systems
   until the appropriate amount of water fit in the pores after running the GROMACS command
@@
   that spent greater than 95\% of their time outside of the distal tail region.
+  %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)
 
@@
 
-  To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
+  To study a given solute, we added 6 solute molecules, equally spaced in $z$, to the
   center of each pore of the equilibrated cross-linked configuration, for a total of 24
-  solutes. Our choice of 6 solutes per pore provides a balance of a useful amount of 
+  solute molecules. We chose 6 solutes per pore to provide a balance of a useful amount of 
   data for generating statistics and a low degree of interaction between solutes (see 
@@
 
+  %MRS2: could potentially make these sections bulleted list, rather than full subsections.
   \subsection{Mean Squared Displacement}\label{method:MSD}
@@
 
-  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear. Therefore, for
+  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear
+  %MRS2: added
+  to within statistical precision.
+  Therefore, for
   the purpose of comparison, we calculated its diffusion constant by fitting a line
@@
 
+  %MRS2: Be more explicit than 'instructive'' - ``Where it help to demonstrate X'' or something like that?
   Where instructive, we differentiated between the length of hops inside
@@
   an RDF averaged over the entire simulation trajectory. We randomly 
-  chose solute RDFs with replacement and averaged them for each bootstrap
-  trial. This approach assumes that solute positions are uncorrelated to
+  %MRS2: tweaked for clarity
+  chose individual solute RDFs with replacement from the set of 24 and averaged 
+  each set for each bootstrap
+  trial in order to generate a distribution from which to calculate uncertainties. 
+  This approach assumes that solute positions are uncorrelated to
   other solutes which we believe is valid due to the low degree of 
@@
   Although the pores are often described as straight, they have a
-  small degree of tortuosity which disrupts the RDF calcuation. We 
+  small degree of tortuosity which disrupts the RDF calculation. We 
   tried to mitigate the effects of tortuosity by calculating the RDF
@@
 %  head group. For each head group, we obtained an RDF averaged over the
-%  entire simulation trajactory. We randomly chose head group RDFs with replacement
-%  and averaged them for each bootsrap trial. This approach assumes that
+%  entire simulation trajectory. We randomly chose head group RDFs with replacement
+%  and averaged them for each bootstrap trial. This approach assumes that
 %  head group positions are uncorrelated.
@@
   density of sodium ions is not at the pore center in the 10 wt\% water system
-  likely because they are still loosely associated with the monomer's carboxylate
+  likely because they are 
+  %MRS2: not that loose
+  %still loosely 
+  associated with the monomer's carboxylate
   head groups.
@@
   the color-coded monomer pictured in the upper right corner of the figure. 
-  All RDFs represent the number of atoms located at a given distance from the
+  RDFs show the average number of atoms located at a given distance from the
   pore center normalized by the volume of the annular bin to which they belong.
@@
 
+  %MRS2: probably would be better to consolidate the information about water in the tails in one place.  Could be here?
+  %MRS2: fundamentally, needs to be explicit justification of the choice to look at transport in the pores alone.
+
   There is an appreciable amount of water that partitions into the distal tail % BJC: defined in methods
@@
 
+  %MRS2: changed tense to present on the paper itself, past on studies leading to the paper.
   We observed transport of sodium, water and 20 other small polar solutes
-  inside the membrane nanopores. First, we will comment on transport of the
+  inside the membrane nanopores. First, we comment on transport of the
   membrane constituents, water and sodium, in a system absent of any additional
-  solutes. Then we will present the general trends that we observe among the
+  solutes. We then present the general trends that we observe among the
   all other solutes studied.
@@
 
-  Sodium coordinates with far less water molecules than it does in bulk solution.
-  Compared to 3.4 coordinated water molecules in bulk solution (see 
-  Section~\ref{method:coordination}), sodium ions in our system, on average,
-  coordinate with about 1.7 water molecules in the 10 wt\% system and 1.2 water
-  molecules in the 5 wt\% system. However, the sodium ions are not undercoordinated
-  since they frequently pair with negatively charged carboxylate head groups.
-  On average, sodium ions coordinate with 1 carboxylate group in the 10 wt\% water
+  %MRS2: rephrasing
+  Sodium coordinates with both water and carboxylate moieties from the head groups in the pores.
+  Sodium coordinates with 3.4 water molecules in bulk solution (see 
+  Section~\ref{method:coordination}), but on average in the pores,
+  coordinates with 1.7 water molecules in the 10 wt\% system and 1.2 water
+  molecules in the 5 wt\% system. The sodium ions additionally coordinate with 1 carboxylate group in the 10 wt\% water
   system and 0.8 carboxylate groups in the 5 wt\% water system. This behavior likely
-  slows their motion considerably.
+  slows the motion of the sodium ions considerably compared to bulk water.
+  %MRS2: is one sodium per carboxylate group correct?
   % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
@@
 
+  %MRS2: some tweaking
   Because the MSD of water in the pores of the 10 wt\% system is significantly
-  higher than that in the tails, we've restricted our studies of transport to 
-  solutes close to the pore center. Transport of solutes in the pores will be the 
-  limiting factor that determines permeability and rejection. Although we showed
-  the opposite in the 5 wt\% water system, water transport is significantly slower
+  higher than that in the tails, we restrict our studies of transport in this paper to 
+  solutes in or near the pore center. Transport of solutes in the pores will be the 
+  limiting factor that determines permeability and rejection. Although tail transport of water in the 
+  the 5 wt\% water system is faster than pore transport, water transport overall is significantly slower
   than in the 10 wt\% system. For practical applications, a membrane with water 
@@
 %  %MRS4: but above would tend to indicate that it moves 51/8 = 6.4 times faster in the tails in 10%? 
-%  %MRS4: think about reading over/describiing the tail water here
+%  %MRS4: think about reading over/describing the tail water here
 %  %MRS4: would probably be useful to the reader to specify that we are neglecting transport in the tails here.
@@
 
-  Like water and sodium above, the MSDs of the solutes studied in this work are 
+  %MRS2: tweak
+  %Like water and sodium above, 
+  As with water and sodium,
+  the MSDs of the solutes studied in this work are 
   significantly larger in the 10 wt\% system than those in the 5 wt\% water 
@@
   Figure~\ref{fig:example_msd} and its shape is sublinear. The long periods
-  of entrapment lead, in part, to this sublinear, and thus subdiffusive, behavior.
+  of entrapment lead in part to this sublinear, and thus subdiffusive, behavior.
 
@@
   head groups, 25\% go to the ether linkages connecting the monomers tails to the 
-  head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molcules in pores 
+  head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molecules in pores 
   carboxylate oxygen atoms in the pore than there are water molecules yet more
@@
   hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}. The 95\textsuperscript{th}
-  percentile of hydrogen bond lifetimes for propylene glycol with monomers is 9.51 ns
+  percentile of hydrogen bond lifetimes for propylene glycol with monomers is 
+  %MRS2: too much precision
+  %9.51
+  9.5 ns
   compared to 7 ns for ethylene glycol. 
   %BJC: not sure of following point is worthwhile 
+  %MRS2: seems OK.
   Somewhat counterintuitively, there is a 
@@
   bonds as 2,3-dimercapto-1-propanol (including all possible hydrogen bonding groups).  % BJC: might be confusing. Maybe refer to figure 6 instead.
-  % BJC: sums are (donate to monomer + recieve from water + donate to water).
+  % BJC: sums are (donate to monomer + receive from water + donate to water).
   % BJC: (31.91 + 17.224 + 3.231) / (13.1 + 7.737 + 0.8965) ~= 2.45.
@@
   solutes in this set show at least a small peak in the pore region which
-  is likely caused by solutes that get trapped in the tail region for 
+  is 
+  %MRS2: can you be more definitive than ``likely caused''?
+likely caused by solutes that get trapped in the tail region for 
   significant periods of time.
@@
   \end{subfigure}
+  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
+  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
   \caption{(a) The MSDs of solutes that can only receive hydrogen bonds are
@@
 
-  Based on these trapping mechanisms, we can suggest modifications that
-  can be made to monomers in order to mitigate or enhance their effect on
-  solute MSDs. Since solutes move slowly while entangled among the monomer
+  Based on these trapping mechanisms, we 
+  %MRS2:
+  %can suggest 
+  may be able to suggest
+  modifications that
+  can be made to monomers in order to 
+  %MRS2: trying something else to emphasize what we are trying to do.
+Can you add a bit more detail so it's not just slowing up or speeding solutes, but slowing or speeding up solutes of a particular type?
+We can emphasize chemical selectivity .
+.
+.
+  %mitigate or enhance their effect on   solute MSDs. 
+  modulate the effect on specific solute MSDs in order to make transport even more 
+  selective for particular solutes.
+  Since solutes move slowly while entangled among the monomer
   tails, one can try to design monomers that better control the partition
@@
 
-  The optimal design of new LLC membranes for a given separation is not obvious.
-  Experimental progress up to this point in time is the culmination of an iterative 
-  educated guess-and-check framework. An array of solute-membrane interactions
-  ensuing from the chemically complex and inhomogeneous LLC membrane structure
-  as well as the complexity of the solutes themselves, have hindered the 
-  establishment of firm design criteria. Our atomistic modeling approach gives
-  us the opportunity to approximate these interactions at the molecular scale
-  so that we can observe them and think more critically about LLC membrane design. 
+  %MRS2: tweaking
+  %The optimal design of new LLC membranes for a given separation is not obvious.
+  The findings here are likely too complex to point towards a clear design for optimal LLC membranes for a 
+  particular separation.   
+  %Experimental progress up to this point in time is the culmination of an iterative 
+  %educated guess-and-check framework. 
+  This work does demonstrate that a large range of solute-membrane interactions
+  resulting from the chemically complex and inhomogeneous LLC membrane structure
+  and the varying chemical functionality of the solutes themselves 
+  %as well as the complexity of the solutes themselves, have hindered the 
+  %establishment of firm design criteria. 
+  gives rise to an immense diversity of transport behavior. This behavior suggests 
+  that a large range of chemical selectivities that may be 
+  possible in self-assembled nanoporous membranes. 
+  Atomistic modeling gives
+  us the opportunity to observe these interactions at the molecular scale, at least approximately,
+  in order to think more critically about nanostructured membrane design. 
 %  We can use insights gained from our model to hypothesize and screen new monomers
@@
 
-  \section*{Acknowledgements}
+  \section*{Acknowledgments}
 
@@
 \end{document}
+
+% LocalWords:  lyotropic LLC solutes solute permeability micropollutants RO NF
+% LocalWords:  groundwaters flowback nanofiltration bruggen Nanostructured feng
+% LocalWords:  nanostructured mesophases Donnan Zhou al Dischinger BJC Hmm Na
+% LocalWords:  selectivities physicochemical nanopores GA pKa's protonated pKa
+% LocalWords:  gallic perrin pka NaGA MeOH URE EtOH acetamide AcN propanol PrOH
+% LocalWords:  butanol BtOH mercaptoethanol EG sulfoxide DMSO PG dimercapto DMP
+% LocalWords:  GLY tetrahydrofuran THF tetrose dimethylformamide DMF AcOH diols
+% LocalWords:  triols MSD solute's readthedocs repo GROMACS gromacs der hess wt
+% LocalWords:  Antechamber bccsym molcharge QUACPAC zhou Resel equil ca gmx COM
+% LocalWords:  solvate solvated Parrinello barostat subdiffusive superdiffusive
+% LocalWords:  subdiffusion CTRW MSDs ageing microfriction Gierer einstein Chan
+% LocalWords:  MSD's comps li Rg appoximation polson bT fr CI Luzar Chandler py
+% LocalWords:  hbonds VMD Roux genion disassociated Clauset martiniano Voloshin
+% LocalWords:  timescales binned RDFs RDF tortuosity carboxylate pdf sodium's
+% LocalWords:  mobilities timescale diffusivity msd tailvpore methanol's tamsds
+% LocalWords:  msds sublinear ztraces COMs alkane COOH HOH hbond immobilization
+% LocalWords:  counterions sulfinyl substituents electronegative COH coord na
+% LocalWords:  Carvajal Wu Shinoda carboxy ATPase rdf counterintuitively Amides
+% LocalWords:  unhindered propanol's butanol's hydrophilicity glycol's Ketones
+% LocalWords:  hybridization amides electronegativity NH ketones Thiols SOH ACI
+% LocalWords:  dimercaptoethanol dimethylsulfoxide rdfs mercaptoethanol's thiol
+% LocalWords:  formamide nondonors nanoporous XSEDE PSC RMACC

### 2019-05-06 Ben_Manuscripts/comps/Outline.tex
notes.
Fixes in response to comments

@@
 
+%MRS: overall, really nice start.
+You can cut back a little on the detail and emphasize a bit more ``This is what the data means and what the consequnces are.
+Need to flesh out objective 3 a more (and objective 4 a bit more).
 \author{Benjamin J. Coscia}
@@
   types of wastewater.
+
+  %MRS: probably can do a little less introduction of the overall membrane needs, as we want to make sure 
+  %MRS: the focus is on the research (thesis, you can include everything).  Can probably hold off that until you get the rest done, then trim as needed for space.
+  %
+  %MRS: remember the purpose of the introduction to any document is to lay out the rules of engagement; you want 
+  %MRS: to raise the questions that the rest of the document will answer.
+  % 
+  %MRS: try to make sure the application motivation and the research described match up when possible.
+  %MRS: if particular applications wouldn't be directly enabled by the research, at least draw to the connection
+  %MRS: i.e. talk about the general tools of computation to understand nanostructured membranes, even if the current
+  %MRS: membranes under development aren't suitable for the particular separations described.
+  %BJC: Something like: The computational techniques developed here are suitable not just for LLC Membranes, but for any nanostructured 
+  % membrane material.
   \begin{itemize}
@@
     mechanisms. 
-    \item Based on this information we can intelligently design new membranes
-    by screening new liquid crystal monomer designs.
-    \item Our most promising designs can be tested experimentally.
+    \item Based on this information we will have a much greater capability
+    intelligently design new membranes by screening new liquid crystal 
+    monomer designs.
+    \item The principles learned can be implemented and tested experimentally.
   \end{itemize}
@@
 
-    Useful molecular-level modeling should incorporate a detailed picture 
+    %MRS: probably should talk about this 1) with proper tense (some of these things have been done) and 2) talk about what YOU are doing, not we.
+I helped design the research, but you carried essentially all of it out!
+If phrased in future tense, committee will be confused, thinking those are things still to be done.
+
+    A useful molecular-level model should incorporate a detailed picture 
     of the nanoscopic pore structure, which is crucial to understanding
     the role of monomer structure in solute transport and membrane design.
-    We will generate simulated X-ray diffraction (XRD) patterns from MD trajectories
-    and compare them to an experimental 2D wide angle X-ray scattering (WAXS)
-    spectrum of a Col\textsubscript{h} phase membrane. We will assess the extent
-    to which we can apply our understanding to the H\textsubscript{II} phase,
-    as well as systems built with alternate monomers.
+    I have created a maximally consistent structural model by comparing 
+    simulated X-ray diffraction (XRD) patterns, generated from MD trajectories,
+    to an experimental 2D wide angle X-ray scattering (WAXS) spectrum of a 
+    Col\textsubscript{h} phase LLC membrane. I have used this model as an 
+    example in order to understand the ease with which we can apply our approach
+    to alternate monomers.
+
+%    shown that we achieve a
+%    similar pore composition regardless of initial configuration which is 
+%    influenced by a number of variables. This implies that our model can
+%    
+%        We will assess the extent to which
+%    we can apply our understanding to the H\textsubscript{II} phase, as well
+%    as systems built with alternate monomers.
 
@@
 
-    We will observe transport of a relatively large set of small polar solutes
-    placed within the H\textsubscript{II} membrane nanopores. We will observe
-    the time series of each solute's position as well as directly measure the
-    physical interactions, such as hydrogen bonding and ion coordination, 
+    I observed the transport of a relatively large set of small polar solutes
+    placed within the H\textsubscript{II} phase membrane nanopores. I analyzed
+    the time series of each solute's position in addition to directly measuring
+    the physical interactions, such as hydrogen bonding and ion coordination, 
     between solutes and LLC monomers.
@@
 
-    We will combine our general knowledge of the solute transport mechanisms
+    I will combine my qualitative knowledge of the solute transport mechanisms
     with simulation data in order to inform a stochastic model. This model
-    should closely reproduce the time series that we observe in our simulations.
-    Due to the low computational cost of a stochastic model relative to 
-    MD simulations, we will be able to project long timescale transport behavior
-    and make well-converged predictions of macroscopic transport properties.
+    should closely reproduce the properties of the time series that we observe 
+    in our simulations. Due to the low computational cost of a stochastic model
+    relative to MD simulations, I will be able to forecast long timescale transport
+    behavior and make well-converged predictions of macroscopic transport properties.
 
@@
     LLC membranes has shifted nearly all focus towards the Q\textsubscript{I}
-    phase due to its more facile synthesis.	Although most of our work has 
-    been applied to the H\textsubscript{II} phase, we expect that much of 
-    the same analyses can be applied to the Q\textsubscript{I} phase. The 
-    biggest challenge will be adapting our techniques to its more complex
-    geometry.
+    phase due to its more facile synthesis.	Although most of my work has 
+    been applied to the H\textsubscript{II} phase, much of the same analyses
+    can be applied to the Q\textsubscript{I} phase. The biggest challenge will
+    be adapting my techniques to its more complex three dimensional geometry.
 
@@
 
+%MRS: overall, good description of wha has been done.  You can cut back a little if space is an issue.  Give the paper citations with the points. 
   \section{Progress to Date}\label{section:progress}
@@
   \end{subfigure}
+  %MRS: not clear what is meant by ``all cases''
   \caption{In all cases, the component radial distribution functions are similar.
@@
   \begin{itemize}
+    %MRS: Talk about data presentations (figures) in the present tense.  
     \item In Figure~\ref{fig:all_msds_10wt}, we plotted the average
@@
   \noindent \textbf{\large Objective 3:} \textit{\large Create a stochastic model} (\textcolor{blue}{\textbf{In Progress}})
-
+  %MRS: yes, needs to be longer.  you can cut back some of the details in objectives 1 and 2. 
   %BJC: This section will get developed further as I think about it more after the paper is submitted

### 2019-05-06 Ben_Manuscripts/transport/Draft.tex
Fixes in response to comments

@@
   membrane's inhomogeneous composition gives rise to radially dependent
-  transport mechanisms with respect to the pore centers. 
-  %MRS3: remove qualifier?
-  %In general, 
-  We 
-  %MRS3: tense
-  %observed 
-  observe
+  transport mechanisms with respect to the pore centers. We observe
   that all solutes perform intermittent hops between lengthy
@@
   All of these separations are possible in part with current commercial
-  membrane separation techniques, but
-  %MRS3: tweaking
-  all still
-  suffer from serious drawbacks. Currently,
-  reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
+  membrane separation techniques, but all still suffer from serious drawbacks.
+  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
   separations of small molecules.~\cite{warsinger_review_2018} RO membranes are
@@
 
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{ortho_view.pdf}
-  \caption{}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{top_view.pdf}
-  \caption{}
-  \end{subfigure}
-  %MRS3: include a bit more description in the caption of what the system: This is the figure that provides the orientation to the readers of what they will be thinking about for the rest of the paper.
-  \caption{In both figures, water molecules that occupy the pores are colored blue,
-  the hydrophilic head groups of the LLC monomers are colored orange with all else
-  colored gray. 
-  %MRS3: probably this point below can be better addressed in the text; looks a little out of place here.
-  We expect that transport will be primarily determined by solute
-  behavior within the pores. 
-  (a) Membrane pores are approximately straight and (b)
-  are packed hexagonally.}\label{fig:membrane_rendering}
-  \end{figure}
-
-  %MRS3: maybe say ``we present studies of''? ``This work'' is the paper, so using past tense is weird.
-  In this work, we have studied the transport mechanisms exhibited by 20 
+  In this work, we present studies of the transport mechanisms exhibited by 20 
   uncharged polar solutes with varying size, chemical functionality and hydrophilic 
@@
   Note that, in order limit our studies to uncharged species, we have only studied
-  %BJC: citations for pKa's
   acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
@@
 
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ortho_view.pdf}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{top_view.pdf}
+  \caption{}
+  \end{subfigure}
+  %MRS3: include a bit more description in the caption of what the system: This is the figure that provides the orientation to the readers of what they will be thinking about for the rest of the paper.
+  %BJC3: gave it another shot
+  \caption{The H\textsubscript{II} phase formed by LLC monomers consists of pores
+  that are approximately straight (a) and packed hexagonally (b). In both figures,
+  water molecules that occupy the pores are colored blue, the hydrophilic head 
+  groups of the LLC monomers are colored orange and all else is colored gray. 
+  The chemical environment within the nanopores is largely determined by the functionality
+  of the head groups. Additionally, there is not a well-defined transition
+  point from the aqueous pore region to the alkane-dense, hydrophobic tail region,
+  generating further complexity.
+  }\label{fig:membrane_rendering}
+  \end{figure}
+
   \begin{table}[h!]
   \centering
-%  \begin{minipage}{.4\textwidth}
-%  \tiny
-%  \begin{tabular}{ |lcc|lcc| }
   \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
@@
   \end{tabular}
-%  \end{minipage}
   \caption{Names of solutes along with their molecular structures and the
@@
   %MRS2: look over this section at the end of the intro again for clarity - some paragraphs are too short (ideas introduced and brushed past quickly) sometimes without strong theses.
-  We first address the structure of the pores formed in the membrane.
-  Previously, we have studied dry membrane systems and some systems with 
-  low water content. We therefore first analyze how the radial density of monomer 
-  components and water change within the pore based on membrane water content.
-
-  We then present our efforts to understand how water partitions within the pores.
-  From a macroscopic perspective, it might make sense to hypothesize that water 
-  spends its time exclusively in the tube-like hydrophilic pore region. Our
-  previous work showed that there is a gradual compositional transition from
-  the hydrophilic to the hydrophobic region which means that solutes may not
-  necessarily stay confined to the centers of the pores or even within the 
-  pore region. 
+  %BJC3: I think these make more sense now.
+
+  We first address the structure of the membrane nanopores. Previously, we
+  studied dry membrane systems and some systems with low water content. We showed
+  that those systems have rather crowded pores with high concentrations of monomer
+  head groups, sodium ions and water, where applicable. Here we build systems with
+  appreciable amounts of water, 5 and 10\% by weight, and analyze how the radial
+  density of monomer components and water change compared to our previous results.
+
+%  We then present our efforts to understand how water partitions within the pores.  
+  We then use the transport rates of water in and out of the pores in order to
+  to justify our study of solute transport restricted to the pore region. From a 
+  macroscopic perspective, it might make sense to hypothesize that water spends its time 
+  exclusively in the tube-like hydrophilic pore region. Our previous work showed
+  that there is a gradual compositional transition from the hydrophilic to the
+  hydrophobic region which means that solutes may not necessarily stay confined
+  to the centers of the pores or even within the pore region. We show that, in 
+  our most viable system, water moves fastest within the pores suggesting that 
+  the pores should be the focus of our mechanistic studies.
+
   %MRS2: ``this information'' is ambiguous. Which information? Also, I'm not sure the paragraph above is enough to 
   %demonstrate why we can/should neglect the tails.
-  We use this information in order to justify our restriction
-  of solute transport studies to just the pore region.
+%  We use this information in order to justify our restriction
+%  of solute transport studies to just the pore region.
 
@@
 
-  In the remainder of the paper, we present our observations 
-  and explanations of the observed transport mechanisms exhibited by water
-  and solutes. 
+  In the remainder of the paper, we describe and quantify three trapping 
+  mechanisms which give rise to subdiffusive solute transport behavior. 
+  We investigated the differences in solute motion, specifically their mean
+  squared displacement (MSD), in conjunction with each solute's size and 
+  chemical functionality. We show how distinct interactions with various
+  monomer components as well as membrane water content hinders the motion 
+  of solutes. We discuss how the interactions between specific solutes and
+  the membrane depend on the solute's chemical functionality.
+%    We present the interactions between solutes, the membrane,
+%  and water in order to determine which mechanism or mechanisms dominate.
+%  present our observations and explanations 
+%  of the observed transport mechanisms exhibited by water and solutes. 
   %MRS2: The thesis of this paragraph could be stronger.
 expand ``pores will restrict motion of the solutes'' a little using the physical details about the pores; paint the picture that will be filled in with detail
-Given that the pores will restrict motion of the solutes, we
-  anticipate that transport will be hindered in some way.
-
-  %MRS2: be consistent on tense.  What is presented in the paper is present tense.  We already studied it, we are presenting it.  
-  We investigate the differences in solute motion, specifically its mean 
-  squared displacement (MSD), based on a solute's size and chemical
-  functionality. We will study the interactions between solutes, the membrane,
-  and water in order to determine which mechanism or mechanisms dominate.
-
-  There are also 
-  %a couple of questions that are beyond
-  several questions beyond
-  the scope of this study.
+  %BJC3: redone above.
+%  Given that the pores will restrict motion of the solutes, we
+%  anticipate that transport will be hindered in some way.
+
+  There are also several questions beyond the scope of this study.
   First, we will not study the concentration dependence of the observed transport
@@
   of solutes in the pores, which could give us a better understanding of 
-  equilibrium solute partitioning. However, this information is 
-  %MRS3: added - there might be mechanisms that only happen with multiple solutes in contact
-  likely
-  not needed
-  to understand the 
-  %MRS3: added
-  principal
-  mechanistic details in various membrane regions. 
-  %MRS3: broke sentence
-  This work 
-  %MRS3: added for flow
-  instead
-  represents a starting point for observing the types of interactions
-  that occur between isolated solutes and the membrane.
+  equilibrium solute partitioning. However, this information is likely
+  not needed to understand the principal mechanistic details in various membrane
+  regions. This work instead represents a starting point for observing the 
+  types of interactions that occur between isolated solutes and the membrane.
 
@@
   Python scripts used to set up systems and conduct post-simulation trajectory 
-  analysis 
-  %MRS2: added to make sure it's clear the basic description is not JUST in the scripts.
-  (as described below and in the supporting information) are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. 
-  %BJC: also link to readthedocs? I have the link in the repo 
-  %MRS2: either is fine. 
-  The appropriate scripts to use for the subsequent calculations are summarized in 
-  Table~\ref{S-table:python_scripts} of the Supporting Information.
-  We ran all molecular dynamics simulations and energy minimizations using GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
+  analysis (as described below and in the supporting information) are available 
+  online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. The 
+  appropriate scripts to use for the subsequent calculations are summarized in 
+  Table~\ref{S-table:python_scripts} of the Supporting Information. We ran all 
+  MD simulations and energy minimizations using GROMACS 2018.3.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
 
@@
   may or may not be experimentally consistent but it is necessary for our results to be 
-  thermodynamically consistent;
-  %MRS3: providing some context
-  otherwise, water would slowly leak from the pore into the tail region over several hundred nanoseconds.
-We iteratively adjusted the pore radius in our systems
+  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
+  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
   until the appropriate amount of water fit in the pores after running the GROMACS command
@@
   studying transport of water in the pores, we limited the calculations to water molecules
-  that spent greater than 95\% of their time outside of the distal tail region.
+  that spent greater than 95\% of their time outside of the distal tail region. We 
+  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
   %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)
+  %BJC3: added reference to later section.
 
@@
 
-  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear
-  %MRS2: added
-  to within statistical precision.
-  Therefore, for
-  the purpose of comparison, we calculated its diffusion constant by fitting a line
-  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
+  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear to within 
+  statistical precision. Therefore, for the purpose of comparison, we calculated its
+  %BJC3: linear within statistical precision --> appears linear? I didn't do any rigorous tests for linearity
+  diffusion constant by fitting a line to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
   is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
@@
   hop lengths.\cite{efron_introduction_1994}
-  % BJC: could add more detail about which algorithm and cost function
-  % penalty I used. Seems unnecessary since it is all in my code.
-  %MRS4: I would put in supporting.
 
@@
 
-  %MRS2: Be more explicit than 'instructive'' - ``Where it help to demonstrate X'' or something like that?
-  Where instructive, we differentiated between the length of hops inside
-  and outside of the pores. For 10 wt\% water systems, we consider a solute
-  to be in the pore if it is within 0.75 nm of a pore center. This radial
-  cut-off maximizes the difference between average hop lengths in and out
-  of the pore. See Section~\ref{S-section:pore-region} of the Supporting
+  We differentiated between the length of hops inside and outside of the 
+  pores. For 10 wt\% water systems, we consider a solute to be in the pore
+  if it is within 0.75 nm of a pore center. This radial cut-off maximizes 
+  the difference between average hop lengths in and out of the pore. 
+  See Section~\ref{S-section:pore-region} of the Supporting
   Information for further details on this optimization.
@@
   an RDF averaged over the entire simulation trajectory. We randomly 
-  %MRS2: tweaked for clarity
   chose individual solute RDFs with replacement from the set of 24 and averaged 
-  each set for each bootstrap
-  trial in order to generate a distribution from which to calculate uncertainties. 
+  each set for each bootstrap trial in order to generate a distribution from 
+  which to calculate uncertainties. 
   This approach assumes that solute positions are uncorrelated to
@@
   density of sodium ions is not at the pore center in the 10 wt\% water system
-  likely because they are 
-  %MRS2: not that loose
-  %still loosely 
-  associated with the monomer's carboxylate
-  head groups.
+  likely because they are associated with the monomer's carboxylate head groups.
 
@@
   %BJC: simulation is extended to smooth out these curves
+  %BJC3: update: got slightly smoother
   \caption{Dry System}\label{fig:component_density_dry}
@@
   for more water.}\label{fig:component_densities}
-  %MRS4: dotted horizontal line not defined.
   \end{figure}
@@
 
-  There is an appreciable amount of water that partitions into the distal tail % BJC: defined in methods
+  There is an appreciable amount of water that partitions into the distal tail
   region of both systems. 28\% and 31\% of the total water is present in the
@@
   Section~\ref{S-section:water_content_equil} of the Supporting Information 
-  for more details on the equilibration that led to this conclusion. The partition
+  for more details on the equilibrations that led to this conclusion. The partition
   is due to a combination of the distal tail region's lower density as well
@@
 
+  We will restrict our studies of transport to solutes and water outside of the 
+  distal tail region because transport is fastest in the pores. We provide more 
+  rigorous justification for this restriction at the end of Section~\ref{section:transport_water_sodium}.
+
   \subsection{Mechanisms Governing Small Solute Transport}\label{section:mechanism_overview}
 
-  %MRS2: changed tense to present on the paper itself, past on studies leading to the paper.
   We observed transport of sodium, water and 20 other small polar solutes
@@
   In the 5 wt\% water system, water molecules that spend the majority of their 
-  time in the distal tail region have MSDs higher than those of water molecules
+  time in the distal tail region have MSDs slightly higher than those of water molecules
   close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
@@
   the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
-  %MRS4: but there is also H-bonding to ions and carboxylate groups, which seems like they should be even stronger than water-water.
   hydrogen bonding between water molecules near the pore center versus those in 
@@
 
-  %MRS2: some tweaking
   Because the MSD of water in the pores of the 10 wt\% system is significantly
@@
 
-  %MRS2: tweak
-  %Like water and sodium above, 
-  As with water and sodium,
-  the MSDs of the solutes studied in this work are 
+  As with water and sodium, the MSDs of the solutes studied in this work are 
   significantly larger in the 10 wt\% system than those in the 5 wt\% water 
@@
   %MRS4: suggest putting something at the beginning of the caption indicating which chemical group it is.
+  %BJC3: added to first sentence of caption
   \caption{(a) The MSD of the simple alcohols decrease as a function of the
@@
   percentile of hydrogen bond lifetimes for propylene glycol with monomers is 
-  %MRS2: too much precision
-  %9.51
-  9.5 ns
-  compared to 7 ns for ethylene glycol. 
-  %BJC: not sure of following point is worthwhile 
-  %MRS2: seems OK.
-  Somewhat counterintuitively, there is a 
+  9.5 ns compared to 7 ns for ethylene glycol. Somewhat counterintuitively, there is a 
   relatively high density of ethylene glycol molecules beyond the head group region
@@
   \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}  %BJC: need error bars!
+  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}
   \caption{}\label{fig:ketone_hbonds}
@@
   solutes in this set show at least a small peak in the pore region which
-  is 
-  %MRS2: can you be more definitive than ``likely caused''?
-likely caused by solutes that get trapped in the tail region for 
+  is caused by solutes that get trapped in the tail region for 
   significant periods of time.
@@
 
-  Based on these trapping mechanisms, we 
-  %MRS2:
-  %can suggest 
-  may be able to suggest
-  modifications that
-  can be made to monomers in order to 
   %MRS2: trying something else to emphasize what we are trying to do.
@@
   %mitigate or enhance their effect on   solute MSDs.   
-  modulate the effect on specific solute MSDs in order to make transport even more 
-  selective for particular solutes.
-  Since solutes move slowly while entangled among the monomer
-  tails, one can try to design monomers that better control the partition
-  of solutes between the pore and tail region. For example, removal of the 
-  ether linkages between the head groups and the monomer tails will decrease
-  the stability of polar molecules near the head groups. Alternatively, one
+  %BJC3: gave it a try
+  Based on these trapping mechanisms, we may be able to suggest modifications
+  that can be made to monomers that will modulate their effect on specific 
+  solute MSDs in order to make transport even more selective for particular 
+  solutes. Since solutes move slowly while entangled among the monomer tails, 
+  one can try to design monomers that better control the partition of solutes
+  between the pore and tail region. For example, removal of the ether linkages between the
+  head groups and the monomer tails will decrease the stability of polar 
+  molecules near the head groups. Solutes that spend a large fraction of their 
+  time in the tails, such as butanol with its high hydrophilic character, could
+  exhibit higher permeabilities from these types of changes. Alternatively, one
   can focus on designing head groups with varying hydrogen bonding capabilities.
-  One can increase the number of hydrogen bonding sites on the head groups
-  in order to trap more solutes, or decrease the number of hydrogen bond sites
-  to trap less. Finally, one can attempt to control the degree to which solutes
-  coordinate with counterions. Changing the size and valence of the counter 
-  ion may offer some interesting behavior. These hypotheses remain to be 
+  One can increase the number of hydrogen bonding sites on the head groups in 
+  order to trap solutes like sugars that have many hydroxyl groups, or decrease
+  the number of hydrogen bond sites to trap less. Finally, one can attempt to control 
+  the degree to which solutes coordinate with counterions. Changing the size
+  and valence of the counterion may offer some interesting behavior. Higher
+  valence counter ions will bind more strongly to solutes which may be a useful
+  way to trap solutes like urea with carbonyl groups. These hypotheses remain to be 
   tested in future simulations of new monomers.
 
-  %MRS2: tweaking
-  %The optimal design of new LLC membranes for a given separation is not obvious.
-  The findings here are likely too complex to point towards a clear design for optimal LLC membranes for a 
-  particular separation.   
-  %Experimental progress up to this point in time is the culmination of an iterative 
-  %educated guess-and-check framework. 
-  This work does demonstrate that a large range of solute-membrane interactions
-  resulting from the chemically complex and inhomogeneous LLC membrane structure
-  and the varying chemical functionality of the solutes themselves 
-  %as well as the complexity of the solutes themselves, have hindered the 
-  %establishment of firm design criteria. 
-  gives rise to an immense diversity of transport behavior. This behavior suggests 
-  that a large range of chemical selectivities that may be 
-  possible in self-assembled nanoporous membranes. 
-  Atomistic modeling gives
-  us the opportunity to observe these interactions at the molecular scale, at least approximately,
-  in order to think more critically about nanostructured membrane design. 
-%  We can use insights gained from our model to hypothesize and screen new monomers
-%  in order to rapidly increase LLC membrane development.
+  The findings here are likely too complex to point towards a clear design of an 
+  optimal LLC membrane for a particular separation. This work does demonstrate
+  that a large range of solute-membrane interactions resulting from the chemically
+  complex and inhomogeneous LLC membrane structure and the varying chemical 
+  functionality of the solutes themselves gives rise to an immense diversity of
+  transport behavior. This behavior suggests that a large range of chemical 
+  selectivities may be possible in self-assembled nanoporous membranes. Atomistic
+  modeling gives us the opportunity to observe these interactions at the molecular
+  scale, at least approximately, so that we can think more critically about 
+  nanostructured membrane design.
 

### 2019-05-07 Ben_Manuscripts/transport/Draft.tex
Updates in response to comments

@@
 
-  %MRS2: rephrasing
-  Sodium coordinates with both water and carboxylate moieties from the head groups in the pores.
-  Sodium coordinates with 3.4 water molecules in bulk solution (see 
-  Section~\ref{method:coordination}), but on average in the pores,
+  Sodium coordinates with both water and carboxylate moieties from the head
+  groups in the pores. Sodium coordinates with 3.4 water molecules in bulk 
+  solution (see Section~\ref{method:coordination}), but on average in the pores,
   coordinates with 1.7 water molecules in the 10 wt\% system and 1.2 water
-  molecules in the 5 wt\% system. The sodium ions additionally coordinate with 1 carboxylate group in the 10 wt\% water
-  system and 0.8 carboxylate groups in the 5 wt\% water system. This behavior likely
-  slows the motion of the sodium ions considerably compared to bulk water.
+  molecules in the 5 wt\% system. The sodium ions additionally coordinate with
+  1 carboxylate group in the 10 wt\% water system and 0.8 carboxylate groups 
+  in the 5 wt\% water system. This behavior likely slows the motion of the 
+  sodium ions considerably compared to bulk water.
   %MRS2: is one sodium per carboxylate group correct?
+  %BJC3: yes, if sodium within cutoff of both oxygens, it is only counted once.
   % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
@@
   water molecules that spend $>$ 95\% of their time \textit{in} the distal tail region, 
-  the MSD of distal tail water decreases 8-fold from 59.6 to 8.2 nm$^2$.
+  the MSD of water is about 8 times lower, decreasing from 59.6 to 8.2 nm$^2$.
 
@@
   %mitigate or enhance their effect on   solute MSDs.   
-  %BJC3: gave it a try
+  %BJC3: gave it a try. Broke into paragraphs
   Based on these trapping mechanisms, we may be able to suggest modifications
@@
   solute MSDs in order to make transport even more selective for particular 
-  solutes. Since solutes move slowly while entangled among the monomer tails, 
-  one can try to design monomers that better control the partition of solutes
-  between the pore and tail region. For example, removal of the ether linkages between the
-  head groups and the monomer tails will decrease the stability of polar 
-  molecules near the head groups. Solutes that spend a large fraction of their 
-  time in the tails, such as butanol with its high hydrophilic character, could
-  exhibit higher permeabilities from these types of changes. Alternatively, one
-  can focus on designing head groups with varying hydrogen bonding capabilities.
-  One can increase the number of hydrogen bonding sites on the head groups in 
-  order to trap solutes like sugars that have many hydroxyl groups, or decrease
-  the number of hydrogen bond sites to trap less. Finally, one can attempt to control 
-  the degree to which solutes coordinate with counterions. Changing the size
-  and valence of the counterion may offer some interesting behavior. Higher
-  valence counter ions will bind more strongly to solutes which may be a useful
-  way to trap solutes like urea with carbonyl groups. These hypotheses remain to be 
-  tested in future simulations of new monomers.
+  solutes.
+
+  Since solutes move slowly while entangled among the monomer tails,
+  and since more than half of the solutes studied spend at least 40\% of their
+  time in the tails, one can try to design monomers that better control the 
+  partition of solutes between the pore and tail region. Solutes move into 
+  the tails due both to their size and hydrophilic character. One may be 
+  able to contain solutes, even small ones like methanol, by increasing
+  the density of monomers close to the head groups through incorporation of 
+  cross-linkable groups in the vicinity. Alternatively, removal of the ether
+  linkages between the head groups and the monomer tails may decrease the 
+  stability of any of the molecules we studied near the head groups and 
+  force them to spend more time within the pore.
+
+  %Solutes that spend a large fraction of their 
+  %time in the tails, such as butanol with its high hydrophilic character, could
+  %exhibit higher permeabilities from these types of changes.
+
+  One can instead focus on designing head groups with varying hydrogen bonding
+  capabilities. Increasing the number of hydrogen bonding sites on the head 
+  groups may enhance the membrane's ability to trap solutes like sugars that 
+  have many hydroxyl groups. Conversely, one can decrease the number of hydrogen
+  bond sites, or replace them with weaker hydrogen bonding atoms like nitrogen, to
+  trap less. In contrast to the system studied here, one can design the head 
+  groups so they can donate hydrogen bonds, which can enhance entrapment of 
+  solutes like acetone that can only accept hydrogen bonds.
+
+  Finally, one can attempt to control the degree to which solutes coordinate
+  with counterions. Increasing the valence of the counterions may cause them
+  to bind more strongly to solutes which may be a useful way to trap 
+  carbonyl-containing solutes like urea for longer periods of time. Of course,
+  an increased valence would require proportionately less total counter ions
+  to balance the system charge which could result in the opposite effect. One
+  could also design the head groups so that counterions are negatively charged
+  which may eliminate their interaction with most solutes.
+
+%  
+%  These hypotheses remain to be tested in future simulations of new
+%  monomers.
 
@@
   optimal LLC membrane for a particular separation. This work does demonstrate
-  that a large range of solute-membrane interactions resulting from the chemically
-  complex and inhomogeneous LLC membrane structure and the varying chemical 
-  functionality of the solutes themselves gives rise to an immense diversity of
+  that there is a large range of solute-membrane interactions resulting from the
+  chemically complex and inhomogeneous LLC membrane structure. The varying 
+  chemical functionality of the solutes themselves gives rise to an immense diversity of
   transport behavior. This behavior suggests that a large range of chemical 

### 2019-05-07 Ben_Manuscripts/transport/Draft.tex
Update tex.

@@
   phase lyotropic liquid crystal (LLC) membranes make them promising
-  for selective separations. In this work, we observe transport
+  %MRS3:
+  candidates
+  for selective separation membranes. 
+  %MRS3: I do worry that the above makes it look like we are not acknowledging the formulation problems.  Maybe something like: 
+  %''models of how chemically selective separation membranes could can function''?
+So the focus is more on the science that these membranes could reveal, rather than saying they are good membranes now?
+Then we talk about new membranes at the end of the introduction.
+Thoughts?
+I didn't go ahead and make  the change since it needs a bit more thought.
+I'm open to other ways to reformulate.
+Some of this thinking will percolate into the rest of the introduction as well.
+  In this work, we observe transport
   of water, sodium ions and 20 small polar solutes within the pores 
@@
   our most viable system, water moves fastest within the pores suggesting that 
-  the pores should be the focus of our mechanistic studies.
+  the 
+  %MR3: added to be more specific - we do look at it getting into the head groups a little.
+  area in and around the central
+  pores should be the focus of our mechanistic studies.
 
@@
   mechanisms which give rise to subdiffusive solute transport behavior. 
-  We investigated the differences in solute motion, specifically their mean
+  We describe the differences in solute motion, specifically their mean
   squared displacement (MSD), in conjunction with each solute's size and 
@@
   the membrane depend on the solute's chemical functionality.
-%    We present the interactions between solutes, the membrane,
-%  and water in order to determine which mechanism or mechanisms dominate.
-%  present our observations and explanations 
-%  of the observed transport mechanisms exhibited by water and solutes. 
-  %MRS2: The thesis of this paragraph could be stronger.
-expand ``pores will restrict motion of the solutes'' a little using the physical details about the pores; paint the picture that will be filled in with detail
-  %BJC3: redone above.
-%  Given that the pores will restrict motion of the solutes, we
-%  anticipate that transport will be hindered in some way.
 
@@
   We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
-  with QUACPAC from Openeye Scientific Software.
+  with QUACPAC from OpenEye Scientific Software.
 
@@
   %BJC3: added reference to later section. 
+  %MRS3: We probably need to mention the amount of water there is; 40% is in the tail.
+We should probably discuss density; that because of the larger tail volume, the density is about 1/X in the distal region than in the pore.
 
@@
   higher than that in the tails, we restrict our studies of transport in this paper to 
-  solutes in or near the pore center. Transport of solutes in the pores will be the 
+  solutes in or near the pore center. Transport of solutes in the pores 
+  %MRS3:
+  %will 
+  is likely to be
+  be the 
   limiting factor that determines permeability and rejection. Although tail transport of water in the 
@@
   \end{subfigure}
+  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
+  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it.
+
   \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
@@
   \end{subfigure}
-  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
-  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
   \caption{(a) The MSDs of solutes that can only receive hydrogen bonds are
@@
   molecules in our model of the H\textsubscript{II} phase formed by the liquid 
-  crystal monomer Na-GA3C11. We found that transport of solutes is primarily
-  governed by water content as well as the chemical functionality of the solute
-  with respect to the chemical structure and functionality of the LLC monomer 
-  and ion present.
-
-  We learned that the MSD of solutes, water and counter ions are highly 
+  crystal monomer Na-GA3C11. We found that transport of solutes is 
+  %MRS3: tweak
+  %primarily
+  governed by both water content as well as the interplay between the chemical functionality of the solute
+  and the chemical functionality of the LLC monomer and ion making up the pore. 
+  We 
+  %MRS3:
+  have shown
+  that the MSD of solutes, water and counter ions are highly 
   dependent on LLC membrane water content. As more water is added to the system, 
-  the pores become less crowded with monomer components. The MSDs of water and
+  the pores become 
+  %less crowded with monomer components. 
+  more dilute in the monomer components.
+  The MSDs of water and
   sodium ions are nearly 2 orders of magnitude larger in the 10 wt\% system 
-  than in the 5 wt\% system. The amount of water in the pores deserves special
+  than in the 5 wt\% system. The amount of water in the pores 
+  %MRS3:
+  thus
+  deserves special
   attention when screening new monomers.
@@
   Alcohols and sugars with multiple hydroxyl groups are very stable
-  in the pore region, but frequent hydrogen bonds with monomer head 
+  in the pore region, but 
+  %frequent 
+  multiple
+  hydrogen bonds with monomer head 
   groups prevent them from diffusing quickly. This effect is reduced when
@@
   solutes. 
-
+  %MRS3: I'd actually suggest connecting these; since above is a thesis statement for the next bit. 
   Since solutes move slowly while entangled among the monomer tails,
@@
 
-  One can instead focus on designing head groups with varying hydrogen bonding
+  One could instead focus on designing head groups with varying hydrogen bonding
   capabilities. Increasing the number of hydrogen bonding sites on the head 
   groups may enhance the membrane's ability to trap solutes like sugars that 
-  have many hydroxyl groups. Conversely, one can decrease the number of hydrogen
-  bond sites, or replace them with weaker hydrogen bonding atoms like nitrogen, to
+  have multiple hydroxyl groups. Conversely, one can decrease the number of hydrogen
+  bonding sites, or replace them with weaker hydrogen bonding atoms like nitrogen, to
   trap less. In contrast to the system studied here, one can design the head 
@@
 % LocalWords:  dimercaptoethanol dimethylsulfoxide rdfs mercaptoethanol's thiol
-% LocalWords:  formamide nondonors nanoporous XSEDE PSC RMACC
+% LocalWords:  formamide nondonors nanoporous XSEDE PSC RMACC TET ribose EAC
+% LocalWords:  berendsen spoel Rahman bulleted Wirtz TBD equilibrations thiols
+% LocalWords:  hbonding DMS linkable permeabilities Calderon Morrin TOC

### 2019-05-07 Ben_Manuscripts/transport/Draft.tex
Add missing files

@@
   phase lyotropic liquid crystal (LLC) membranes make them promising
-  %MRS3:
-  candidates
-  for selective separation membranes. 
-  %MRS3: I do worry that the above makes it look like we are not acknowledging the formulation problems.  Maybe something like: 
-  %''models of how chemically selective separation membranes could can function''?
-So the focus is more on the science that these membranes could reveal, rather than saying they are good membranes now?
-Then we talk about new membranes at the end of the introduction.
-Thoughts?
-I didn't go ahead and make  the change since it needs a bit more thought.
-I'm open to other ways to reformulate.
-Some of this thinking will percolate into the rest of the introduction as well.
+  candidates for selective separation membranes. 
+  %MRS3: I do worry that the above makes it look like we are not acknowledging
+  %the formulation problems.  Maybe something like: ''models of how chemically
+  %selective separation membranes could can function''?  So the focus is more
+  %on the science that these membranes could reveal, rather than saying they
+  %are good membranes now?  Then we talk about new membranes at the end of the
+  %introduction. Thoughts? I didn't go ahead and make  the change since it
+  %needs a bit more thought.  I'm open to other ways to reformulate.  Some of
+  %this thinking will percolate into the rest of the introduction as well.
   In this work, we observe transport
@@
 
+% re-outline from here.
+
   Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
@@
   rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
+
+  Under the right conditions, amphiphilic molecules can self-assemble
+  into ordered nanostructures that may be capable of performing highly selective separations.
+  \begin{itemize}
+    \item Uniform-sized pores characteristic of these systems enforce a 
+    molecular-size cut-off, eliminating issues related to the polydisperity 
+    of NF pores.
+    \item By controlling the chemical identity of moeties inside the pores, 
+    it may be possible to tune these types of materials for solute-specific
+    separations.
+  \end{itemize}
+
+  Lyotropic liquid crystals (LLCs) are known to form the type I bicontinuous
+  (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II}) phases.
+  \begin{itemize}
+	\item When cross-linked, these materials can function as separations
+	 membranes.
+	\item The H\textsubscript{II}
+  \end{itemize}
+
 %  Zhou et al. demonstrated complete rejection
@@
   offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
-
+%============= 
 %  The separation performance of these membranes has been 

### 2019-05-07 LLC_Membranes/timeseries/forecast_ctrw.py

@@ -125,14 +125,14 @@ class System(object):
         # exit()
 
         # plot first order difference histogram
-        nbins = 100
-        plt.hist((self.com[1:, :, 2] - self.com[:-1, :, 2]).flatten(), bins=nbins, density=True)
-        plt.tick_params(labelsize=14)
-        plt.xlabel('$z$-direction hop length (nm)', fontsize=14)
-        plt.ylabel('Frequency', fontsize=14)
-        plt.tight_layout()
-        plt.show()
-        exit()
+        # nbins = 100
+        # plt.hist((self.com[1:, :, 2] - self.com[:-1, :, 2]).flatten(), bins=nbins, density=True)
+        # plt.tick_params(labelsize=14)
+        # plt.xlabel('$z$-direction hop length (nm)', fontsize=14)
+        # plt.ylabel('Frequency', fontsize=14)
+        # plt.tight_layout()
+        # plt.show()
+        # exit()
 
         # plot first order differences
         #plt.plot((self.com[1:, 1, 2] - self.com[:-1, 1, 2]))
@@ -146,16 +146,16 @@ class System(object):
         # exit()
 
         # create timeseries by randomly drawing from unconditional pdf of hop lengths
-        p = (self.com[1:, :, 2] - self.com[:-1, :, 2]).flatten()
-        for i in range(10):
-            t = np.random.choice(p, size=2000)
-            plt.plot(np.linspace(0, 1000, len(t)), np.cumsum(t), linewidth=2)
-            plt.tick_params(labelsize=14)
-            plt.xlabel('Time (ns)', fontsize=14)
-            plt.ylabel('$z$-coordinate (nm)', fontsize=14)
-            plt.tight_layout()
-            plt.show()
-        exit()
+        # p = (self.com[1:, :, 2] - self.com[:-1, :, 2]).flatten()
+        # for i in range(10):
+        #     t = np.random.choice(p, size=2000)
+        #     plt.plot(np.linspace(0, 1000, len(t)), np.cumsum(t), linewidth=2)
+        #     plt.tick_params(labelsize=14)
+        #     plt.xlabel('Time (ns)', fontsize=14)
+        #     plt.ylabel('$z$-coordinate (nm)', fontsize=14)
+        #     plt.tight_layout()
+        #     plt.show()
+        # exit()
 
         if ma:
             self.calculate_moving_average(ma)
@@ -544,6 +544,8 @@ class System(object):
[…]

### 2019-05-07 Ben_Manuscripts/transport/Draft.tex
Beginnings of intro outline

@@
 
-  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
-  membranes are nanostructured membranes that may be able to achieve the
-  selectivity of RO membranes while maintaining the high permeability
-  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
-  phase is formed when LLC monomers self-assemble into hexagonally packed
-  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
-  cross-linking of the hexagonal mesophases yields a mechanically strong
-  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
-  enforce a strict molecular-size cut-off while the hexagonal geometry is 
-  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
-  because the LLC monomers are salts, Donnan exclusion plays a role in 
-  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
+%  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
+%  membranes are nanostructured membranes that may be able to achieve the
+%  selectivity of RO membranes while maintaining the high permeability
+%  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
+%  phase is formed when LLC monomers self-assemble into hexagonally packed
+%  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
+%  cross-linking of the hexagonal mesophases yields a mechanically strong
+%  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
+%  enforce a strict molecular-size cut-off while the hexagonal geometry is 
+%  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
+%  because the LLC monomers are salts, Donnan exclusion plays a role in 
+%  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
 
   Under the right conditions, amphiphilic molecules can self-assemble
-  into ordered nanostructures that may be capable of performing highly selective separations.
+  into ordered nanostructures that may be capable of performing highly
+  selective separations.
   \begin{itemize}
-    \item Uniform-sized pores characteristic of these systems enforce a 
-    molecular-size cut-off, eliminating issues related to the polydisperity 
-    of NF pores.
+    \item The uniform-sized aqueous pores characteristic of these types of
+    systems enforce a molecular-size cut-off, eliminating issues related to the
+    polydisperity of NF pores.
     \item By controlling the chemical identity of moeties inside the pores, 
@@
 
-  Lyotropic liquid crystals (LLCs) are known to form the type I bicontinuous
-  (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II}) phases.
+  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I 
+  bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
+  phases.
   \begin{itemize}
@@
 	 membranes.
-	\item The H\textsubscript{II}
+	\item The H\textsubscript{II} phase has hexagonally packed, straight
+	pores which is the ideal geometry for high throughtput separations.
+	\item However, the synthesis of H\textsubscript{II} membranes with 
+	highly aligned hexagonal mesophases has been a challenge that has 
+	prevented this type of membrane's viability.
+	\item The Q\textsubscript{I} has been studied with much more 
+	success. 
   \end{itemize}
@@
 
-  In addition to geometric factors which make H\textsubscript{II} membranes
-  ideal for selective separations, they have the potential to further disrupt
-  conventional membrane separation techniques by being selective based not
-  only on solute size and charge, but on chemical functionality as well. 
-  The functional LLC monomer head groups that occupy the pore region of the
-  membrane can interact with solutes. Dischinger et al.~studied the 
-  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
-  similar pore topology to the H\textsubscript{II} phase, but a more 
-  tortuous geometry, and observed a range of selectivities dependent on the
-  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
-  design of LLC monomers have the potential to help us tailor membranes for 
-  solute-specific separations.
-
-  While H\textsubscript{II} membranes have been synthesized and characterized
-  in a lab setting, there is a limit to the level of detail that can be obtained 
-  from experiment. These membranes have been primarily characterized with 
-  size-exclusion experiments which can give an estimate of pore size as well as
-  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
-  However, size exclusion does not appear to be sufficient to fully describe LLC
-  membranes. Dischinger et al. studied a similar membrane and found that they do
-  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
-  between various solute physicochemical properties and observed solute rejection. 
-  Although there was some agreement with their empirical model, it does not
-  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
+%  In addition to geometric factors which make H\textsubscript{II} membranes
+%  ideal for selective separations, they have the potential to further disrupt
+%  conventional membrane separation techniques by being selective based not
+%  only on solute size and charge, but on chemical functionality as well. 
+%  The functional LLC monomer head groups that occupy the pore region of the
+%  membrane can interact with solutes. Dischinger et al.~studied the 
+%  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
+%  similar pore topology to the H\textsubscript{II} phase, but a more 
+%  tortuous geometry, and observed a range of selectivities dependent on the
+%  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
+%  design of LLC monomers have the potential to help us tailor membranes for 
+%  solute-specific separations.
+
+%  While H\textsubscript{II} membranes have been synthesized and characterized
+%  in a lab setting, there is a limit to the level of detail that can be obtained 
+%  from experiment. These membranes have been primarily characterized with 
+%  size-exclusion experiments which can give an estimate of pore size as well as
+%  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
+%  However, size exclusion does not appear to be sufficient to fully describe LLC
+%  membranes. Dischinger et al. studied a similar membrane and found that they do
+%  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
+%  between various solute physicochemical properties and observed solute rejection. 
+%  Although there was some agreement with their empirical model, it does not
+%  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
 %============= 

### 2019-05-08 Ben_Manuscripts/transport/Draft.tex
Intro edits

@@
 
-  The uniform size and complex chemical topology of the pores that 
-  constitute cross-linked inverted hexagonal (H\textsubscript{II})
-  phase lyotropic liquid crystal (LLC) membranes make them promising
-  candidates for selective separation membranes. 
+  The uniform size and complex chemical topology of the pores formed by
+  self-assembled amphiphilic molecules such as liquid crystals make them
+  promising candidates for selective separations.
+  %that 
+  %constitute cross-linked inverted hexagonal (H\textsubscript{II})
+  %phase lyotropic liquid crystal (LLC) membranes make them promising
+  %candidates for selective separation membranes. 
   %MRS3: I do worry that the above makes it look like we are not acknowledging
@@
   %this thinking will percolate into the rest of the introduction as well.
-  In this work, we observe transport
-  of water, sodium ions and 20 small polar solutes within the pores 
-  of an LLC membrane using atomistic molecular simulations. We 
-  find that the transport of a species is dependent not only on 
-  molecular size, but on chemical functionality as well. The 
-  membrane's inhomogeneous composition gives rise to radially dependent
-  transport mechanisms with respect to the pore centers. We observe
-  that all solutes perform intermittent hops between lengthy
-  periods of entrapment. Three different trapping mechanisms are 
-  responsible for this behavior. First, solutes that drift
-  out of the pore can become entangled among the dense monomer
-  tails. Second, solutes can donate hydrogen bonds to the monomer
-  head groups. Third, solutes can coordinate with sodium counter ions.
-  The degree to which a solute is affected by each mechanism is 
-  dependent on the chemical functionality of the solute. Using the
-  insights developed in this study, we can begin to think about 
-  how to redesign existing LLC membranes in order to perform 
-  solute-specific separations.
+  In this work, we observe transport of water, sodium ions and 20 small polar
+  solutes within the pores of a lyotropic liquid crystal (LLC) membrane using
+  atomistic molecular simulations. We find that the transport of a species is
+  dependent not only on molecular size, but on chemical functionality as well.
+  The membrane's inhomogeneous composition gives rise to radially dependent
+  transport mechanisms with respect to the pore centers. We observe that all
+  solutes perform intermittent hops between lengthy periods of entrapment. Three
+  different trapping mechanisms are responsible for this behavior. First, solutes
+  that drift out of the pore can become entangled among the dense monomer tails.
+  Second, solutes can donate hydrogen bonds to the monomer head groups. Third,
+  solutes can coordinate with sodium counter ions.  The degree to which a solute
+  is affected by each mechanism is dependent on the chemical functionality of the
+  solute. Using the insights developed in this study, we can begin to think about
+  how to redesign existing LLC membranes in order to perform solute-specific
+  separations.
 
@@
 
-  Under the right conditions, amphiphilic molecules can self-assemble
-  into ordered nanostructures that may be capable of performing highly
-  selective separations.
+  %BJC4: generalized to amphiphilic self-assembled structures.
+  Under the right conditions, amphiphilic molecules can self-assemble into
+  ordered nanostructures that may be capable of performing highly selective
+  separations with permeabilities comparable to NF.
   \begin{itemize}
@@
     polydisperity of NF pores.
-    \item By controlling the chemical identity of moeties inside the pores, 
-    it may be possible to tune these types of materials for solute-specific
-    separations.
+    \item In addition to size-exclusion, it may be possible to control the
+    chemical environment within the nanopores by altering the identities of the
+    hydrophilic moeties that form the pores, affording solute-specific separations.
   \end{itemize}
 
+  %BJC4: bring it back to LLCs but don't make it seem like HII is the best
   Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I 
@@
   \begin{itemize}
-	\item When cross-linked, these materials can function as separations
-	 membranes.
+	\item When cross-linked, these materials can function as mechanically
+	strong separations membranes.
 	\item The H\textsubscript{II} phase has hexagonally packed, straight
@@
 	highly aligned hexagonal mesophases has been a challenge that has 
-	prevented this type of membrane's viability.
-	\item The Q\textsubscript{I} has been studied with much more 
-	success. 
+	prevented the material's viability as a separations membrane.
+	\item The Q\textsubscript{I} consists of a three dimensional network
+	of tortuous and interconnected pores. 
+	\item It's more facile synthesis has yielded it more success
+	\item The latest Q\textsubscript{I} phase membranes have been shown
+	to exhibit selectivities and permeabilities higher than commercial
+	RO and NF membranes.
+  \end{itemize}
+
+  % Highlight that QI has the best chance.
+  Although Q\textsubscript{I} membranes have shown promising results, it
+  is not clear how to controllably design them for specific separations
+  beyond what has already been achieved.
+  \begin{itemize}
+    \item Dischinger et al. found that they do not separate purely on the basis
+    of size.~\cite{dischinger_effect_2017} 
+    \item Empirical modeling revealed correlations between various solute
+    physicochemical properties and observed solute rejection. 
+    \item Although there was some agreement with their empirical model, it does not
+    offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
   \end{itemize}
@@
   Molecular dynamics (MD) simulations can give us mechanistic insights with
-  atomistic resolution so that we can provide detailed descriptions of
-  small solute transport within LLC membrane nanopores and intelligently design new membranes for 
-  solute-specific separations. In our previous work, we used MD simulations to 
-  determine the most likely structure of the hexagonal phase formed by the monomer
-  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
-  We developed techniques to simulate the hexagonal phase formed by neat 
-  monomer as well as with varying amounts of water in the pores.
-
+  atomistic resolution so that we can provide detailed descriptions of small
+  solute transport within LLC membrane nanopores and intelligently design new
+  membranes for solute-specific separations. In our previous work, we used MD
+  simulations to determine the most likely structure of the hexagonal phase
+   formed by the monomer Na-GA3C11, expanding upon the most recent experimental
+  characterization.~\cite{coscia_understanding_2018,feng_thin_2016} We developed
+  techniques to simulate the hexagonal phase formed by neat monomer as well as
+  with varying amounts of water in the pores.
+
+  %BJC4: also edited here to help with the flow.
   In this work, we present studies of the transport mechanisms exhibited by 20 
   uncharged polar solutes with varying size, chemical functionality and hydrophilic 
-  character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
-  the membrane in which we placed solutes. We have listed the solutes studied along with the abbreviations that
-  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
-  Note that, in order limit our studies to uncharged species, we have only studied
-  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
-  pKa of acetic acid is 4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} 
-  Assuming that the pKa of gallic acid is similar to NaGA3C11, it is possible
-  for our sodium salted monomer to exist at the same time as protonated acetic
-  acid. In any case, we are more interested in mechanisms of interaction with
-  specific chemical functionality more than the behavior of specific molecules.
+  character within the pores of an H\textsubscript{II} phase LLC. The pores of the 
+  H\textsubscript{II} phase have a similar topology to the Q\textsubscript{I} phase but
+  is a simpler geometry to model. In future studies, we will extend our techniques to
+  the Q\textsubscript{I} phase.
+
+  %BJC4: not sure if I should add a thesis to this paragraph, reattach above, or just
+  % leave as is since it's informational.
+  Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of the
+  membrane in which we placed solutes. We have listed the solutes studied along
+  with the abbreviations that we will use in the charts for the remainder of this
+  paper in Table~\ref{table:abbreviations}. Note that, in order limit our
+  studies to uncharged species, we have only studied acetic acid in its
+  protonated form. The pKa of gallic acid is 4.40 while the pKa of acetic acid is
+  4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} Assuming that the pKa of
+  gallic acid is similar to NaGA3C11, it is possible for our sodium salted
+  monomer to exist at the same time as protonated acetic acid. In any case, we
+  are more interested in mechanisms of interaction with specific chemical
+  functionality more than the behavior of specific molecules.
 

### 2019-05-08 Ben_Manuscripts/transport/Supporting_Information.tex
added a couple of comments/corrections.

@@
   GROMACS command \texttt{gmx solvate} places water molecules in proximity to
-  other atoms based on their van der waals radii and therefore does
+  other atoms based on their van der Waals radii and therefore does
   a decent job of preventing equilibration issues. This also means that the
-  intial pore radius dictates the water content of the pore. We can however, put
+  initial pore radius dictates the water content of the pore. We can however, put
   arbitrary amounts of water into the tail region. We chose to test systems with
@@
   built with 6 solutes per pore. Even methanol, which interacts with other same-solute
-  molcules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interation}
+  molecules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interaction}
   \end{figure}
@@
 %  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
-%  the majority of the trapping occurence between 400 and 600 ns. Regions
+%  the majority of the trapping occurrence between 400 and 600 ns. Regions
 %  highlighted red or blue indicate times when methanol's oxygen atom is within 
@@
 %  \end{equation}
-%  For brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq
+%  For Brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq
 %  1$, the particle of interest exhibits anomalous diffusion. Values of $\alpha$
@@
 %  observable. Examples of anomalous diffusion processes that are ergodic include
-%  random walks on fractals (RWF) and fractional brownian motion (FBM).
+%  random walks on fractals (RWF) and fractional Brownian motion (FBM).
 %  Non-ergodic systems generally give rise to CTRWs with the possibility of
@@
 %
-%  Based on the previous two sections, our model can likey be studied as a CTRW. 
+%  Based on the previous two sections, our model can likely be studied as a CTRW. 
 %  However, it is still possible that our CTRW model might also be convoluted with
@@
 \end{document}
+
+% LocalWords:  LLC solutes py solvated GROMACS mdp solute ctrw GitHub equil xtc
+% LocalWords:  kinetically gro gmx solvate der Waals wt PR savename pl pr trr
+% LocalWords:  plateaued xlinked BJC MSDs Gierer Wirtz MSD SE tamsds hbond dist
+% LocalWords:  tetrose ribose glcyol png tortuosity nn methanol's THF ca Meroz
+% LocalWords:  Mercaptoethanol's Mercaptoethanol Complexation complexation msd
+% LocalWords:  Sokolov superdiffusion subdiffusion nojump ETH nboot RWF FBM npt
+% LocalWords:  subdiffusive CTRWs traj fracshow nanopore RW hoppy ACF brownian

### 2019-05-08 Ben_Manuscripts/transport/cover_letter.tex
updated tex.

@@
 
-	In this article, we use molecular dynamics (MD) simulations in order to observe 
-	transport of small solutes in an inverted hexagonal (H\textsubscript{II}) phase 
-	self-assembled lytropic liquid crystal (LLC) polymer membrane. Recently, we 
-	published our first article on this subject in which we built and characterized
-	an atomistic molecular model of an LLC membrane that is maximally consistent with experimental
-	observations. By observing transport of solutes within a similar model, we can 
-	learn the optimal ways to tune the shape, size and chemical functionality
-	of LC monomers in order to intelligently design the pore environment and facilitate
-	solute-specific separations.
+	In this article, we use molecular dynamics (MD) simulations in
+        order to observe transport of small solutes in an inverted
+        hexagonal (H\textsubscript{II}) phase self-assembled lytropic
+        liquid crystal (LLC) polymer membrane. This is one of the
+        first, and far the most extensive, uses of molecular dynamics
+        to understand the molecular details of transport in such
+        chemical complex nanostructured channels. Most importantly, we
+        show how such channels can give rise to selective transport
+        that is not simply size dependent, but also varies according
+        to chemical functionality of the solutes.
 
-	In this work, we observe and quantify transport of water, sodium and 20 small
-	polar solutes within the pores of our atomistic H\textsubscript{II} phase LLC membrane
-	model. In general, all solutes exhibit subdiffusive transport behavior
-	characterized by intermittent hops between long periods of entrapment. However, 
-	due the pores' inhomogeneous architecture, we observed 3 different mechanisms
-	of entrapment. First, solutes can diffuse out of the pores and become entangled 
-	between tails. Second, many of the solutes are capable of donating hydrogen bonds
-	to monomer head groups for extended periods of time. Finally, solutes can associate
-	with monomer head group counter-ions within nanopores. Each solute is influenced 
-	by each mechanism to varying degrees dependent on its size and chemical 
-	functionality. We begin our discussion with a broad description of these mechanisms
-	in the context of all solutes before restricting the discussion to more detailed 
-	analyses of subsets of chemically-similar solutes.
+        Recently, we characterized an atomistic molecular model of an
+        LLC membrane that is maximally consistent with experimental
+        observations (Coscia et al. \textit{J. Phys. Chem. B}, 123,
+        289--309 (2019)). In this work, we observe and quantify
+        transport of water, sodium and 20 small polar solutes within
+        the pores of our atomistic H\textsubscript{II} phase LLC
+        membrane model. In general, all solutes exhibit subdiffusive
+        transport behavior characterized by intermittent hops between
+        long periods of entrapment. However, due the pores'
+        inhomogeneous architecture, we observed 3 different mechanisms
+        of entrapment. First, solutes can diffuse out of the pores and
+        become entangled between tails. Second, many of the solutes
+        are capable of donating hydrogen bonds to monomer head groups
+        for extended periods of time. Finally, solutes can associate
+        with monomer head group counter-ions within nanopores. Each
+        solute is influenced by each mechanism to varying degrees
+        dependent on its size and chemical functionality. We begin our
+        discussion with a broad description of these mechanisms in the
+        context of all solutes before restricting the discussion to
+        more detailed analyses of subsets of chemically-similar
+        solutes.
 
@@
 		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
-		and various	nanostructured materials (Northeastern Univerity, 617-373-8619 	
+		and various	nanostructured materials (Northeastern University, 617-373-8619 	
 		\href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})

### 2019-05-08 Ben_Manuscripts/transport/Draft.tex
updated tex.
Moved spatial density figure to main text

@@
 \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
-
-% MRS2: I think it would be useful to have a picture of the pores to 
-% allow people to visualize what was going on. ToC might be good, 
-% but I think that as people read, they need to see the 3D picture 
-% as well to think through things.
 
@@
   ordered nanostructures that may be capable of performing highly selective
-  separations with permeabilities comparable to NF.
-  \begin{itemize}
-    \item The uniform-sized aqueous pores characteristic of these types of
-    systems enforce a molecular-size cut-off, eliminating issues related to the
-    polydisperity of NF pores.
-    \item In addition to size-exclusion, it may be possible to control the
-    chemical environment within the nanopores by altering the identities of the
-    hydrophilic moeties that form the pores, affording solute-specific separations.
-  \end{itemize}
+  separations with permeabilities comparable to NF.~\cite{alexandridis_amphiphilic_2000}
+  The uniform-sized aqueous pores characteristic of these types of systems 
+  enforce a molecular-size cut-off, eliminating issues related to the 
+  polydisperity of NF pores.~\cite{zhou_supported_2005} In addition to size-exclusion,
+  it may be possible to control the chemical environment within the nanopores by
+  altering the identities of the hydrophilic moieties that form the pores, 
+  affording solute-specific separations.~\cite{dischinger_effect_2017}
 
@@
   bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
-  phases.
-  \begin{itemize}
-	\item When cross-linked, these materials can function as mechanically
-	strong separations membranes.
-	\item The H\textsubscript{II} phase has hexagonally packed, straight
-	pores which is the ideal geometry for high throughtput separations.
-	\item However, the synthesis of H\textsubscript{II} membranes with 
-	highly aligned hexagonal mesophases has been a challenge that has 
-	prevented the material's viability as a separations membrane.
-	\item The Q\textsubscript{I} consists of a three dimensional network
-	of tortuous and interconnected pores. 
-	\item It's more facile synthesis has yielded it more success
-	\item The latest Q\textsubscript{I} phase membranes have been shown
-	to exhibit selectivities and permeabilities higher than commercial
-	RO and NF membranes.
-  \end{itemize}
+  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010} 
+  When cross-linked, these materials can function as mechanically
+  strong separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
+  phase has hexagonally packed, straight pores which is the ideal geometry 
+  for high throughtput separations. However, the synthesis of H\textsubscript{II}
+  membranes with highly aligned hexagonal mesophases has been a challenge that
+  has been met with limited success and has prevented the material's viability 
+  as a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The Q\textsubscript{I} 
+  consists of a three dimensional network of tortuous and interconnected pores. 
+  It's more facile synthesis has yielded it more success. The latest 
+  Q\textsubscript{I} phase membranes have been shown to exhibit selectivities
+  higher than commercial NF and RO membranes permeabilities higher than commercial
+  RO membranes.~\cite{dischinger_application_2017}
 
@@
   is not clear how to controllably design them for specific separations
-  beyond what has already been achieved.
-  \begin{itemize}
-    \item Dischinger et al. found that they do not separate purely on the basis
-    of size.~\cite{dischinger_effect_2017} 
-    \item Empirical modeling revealed correlations between various solute
-    physicochemical properties and observed solute rejection. 
-    \item Although there was some agreement with their empirical model, it does not
-    offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
-  \end{itemize}
+  beyond what has already been achieved. Dischinger et al. found that they
+  do not separate purely on the basis of size. Empirical modeling revealed
+  correlations between various solute physicochemical properties and 
+  observed solute rejection. Although there was some agreement with their
+  empirical model, it does not offer a sufficiently detailed explanation
+  of governing molecular interactions.~\cite{dischinger_effect_2017}
 
@@
   for more details on the equilibrations that led to this conclusion. The partition
-  is due to a combination of the distal tail region's lower density as well
-  as oxygen atoms at the ends of each monomer tail which can further stabilize
-  water molecules. See Figure~\ref{S-fig:total_density} of the Supporting 
-  Information for a graphical illustration of this point.
+  is due to a combination of the distal tail region's lower density (see 
+  Figure~\ref{fig:total_density})as well as oxygen atoms at the ends of each
+  monomer tail which can further stabilize water molecules.
+
+  %See Figure~\ref{S-fig:total_density} of the Supporting 
+  %Information for a graphical illustration of this point.
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
+  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
+  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
+  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \vspace{-0.5cm}
+  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
+  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
+  \end{subfigure}
+  \caption{Looking down at the $xy$ plane of the LLC membranes, the lowest density regions
+  of both membranes are in the pore center and in the tail region, furthest from the pore
+  center (a \& c). Water is densest in the low density regions (b \& d).}\label{fig:total_density}
+  \end{figure}
 
@@
   solute MSDs in order to make transport even more selective for particular 
-  solutes. 
-  %MRS3: I'd actually suggest connecting these; since above is a thesis statement for the next bit. 
-  Since solutes move slowly while entangled among the monomer tails,
+  solutes. Since solutes move slowly while entangled among the monomer tails,
   and since more than half of the solutes studied spend at least 40\% of their

### 2019-05-08 Ben_Manuscripts/transport/Supporting_Information.tex
Moved spatial density figure to main text

@@
 
-\title{Supporting Information: Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Supporting Information: Chemically Selective Transport in a Cross-linked 
+H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
 
-  \clearpage
-  \section{Total Membrane Density}\label{section:total_density}
-
-  In our simulations, we observe that water partitions into the tail region
-  because of the tails' low density. We plotted the density of all atoms in 
-  the system as function of their $xy$ positions within the unit cell. The 
-  pore centers of the 5 and 10 wt \% water systems have a relatively low density
-  that is comparable to the density in the tails far from the pore center
-  (see figures~\ref{fig:total_density_5wt} and~\ref{fig:total_density_10wt}).
-  The density is highest near the middle of the tails. The observed density distribution
-  is necessary in order for the wedge-shaped monomers to fill space and stay in
-  the hexagonal phase. Accordingly, water is densest in the pore center and at 
-  the tail ends (see figures~\ref{fig:total_water_density_5wt} 
-  and~\ref{fig:total_water_density_10wt}). Very little water is present in the 
-  dense mid-tail region.
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
-  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
-  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
-  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
-  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
-  \end{subfigure}
-  \caption{The lowest density regions of both membranes are in the pore center and in the
-  tail region, furthest from the pore center (a \& c). Water is densest in the low density
-  regions (b \& d).}\label{fig:total_density}
-  \end{figure}
+%  \clearpage
+%  \section{Total Membrane Density}\label{section:total_density}
+%  BJC: moved to main text
+%  
+%  In our simulations, we observe that water partitions into the tail region
+%  because of the tails' low density. We plotted the density of all atoms in 
+%  the system as function of their $xy$ positions within the unit cell. The 
+%  pore centers of the 5 and 10 wt \% water systems have a relatively low density
+%  that is comparable to the density in the tails far from the pore center
+%  (see figures~\ref{fig:total_density_5wt} and~\ref{fig:total_density_10wt}).
+%  The density is highest near the middle of the tails. The observed density distribution
+%  is necessary in order for the wedge-shaped monomers to fill space and stay in
+%  the hexagonal phase. Accordingly, water is densest in the pore center and at 
+%  the tail ends (see figures~\ref{fig:total_water_density_5wt} 
+%  and~\ref{fig:total_water_density_10wt}). Very little water is present in the 
+%  dense mid-tail region. 
+%  
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
+%  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
+%  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
+%  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
+%  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
+%  \end{subfigure}
+%  \caption{The lowest density regions of both membranes are in the pore center and in the
+%  tail region, furthest from the pore center (a \& c). Water is densest in the low density
+%  regions (b \& d).}\label{fig:total_density}
+%  \end{figure}
 

### 2019-05-08 Ben_Manuscripts/transport/Draft.tex
edits after full read through

@@
   membrane separation techniques, but all still suffer from serious drawbacks.
-  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
-  separations of small molecules.~\cite{warsinger_review_2018} RO membranes are
-  typically dense polymer matrices that separate solutes based on differences in
-  their solubility and permeability in the membrane
+  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial
+  membrane separations of small molecules.~\cite{warsinger_review_2018} RO
+  membranes are typically dense polymer matrices that separate solutes based on
+  differences in their solubility and permeability in the membrane
   material.~\cite{fritzmann_state---art_2007} Although they can perform highly
-  selective separations, high feed pressures and thus large amounts of energy
-  are necessary in order to generate a useful permeate
+  selective separations, high feed pressures and thus large amounts of energy are
+  necessary in order to generate a useful permeate
   flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
@@
   ordered nanostructures that may be capable of performing highly selective
-  separations with permeabilities comparable to NF.~\cite{alexandridis_amphiphilic_2000}
-  The uniform-sized aqueous pores characteristic of these types of systems 
-  enforce a molecular-size cut-off, eliminating issues related to the 
-  polydisperity of NF pores.~\cite{zhou_supported_2005} In addition to size-exclusion,
-  it may be possible to control the chemical environment within the nanopores by
-  altering the identities of the hydrophilic moieties that form the pores, 
-  affording solute-specific separations.~\cite{dischinger_effect_2017}
+  separations with permeabilities comparable to
+  NF.~\cite{alexandridis_amphiphilic_2000} The uniform-sized aqueous pores
+  characteristic of these types of systems enforce a molecular-size cut-off,
+  eliminating issues related to the polydisperity of NF
+  pores.~\cite{zhou_supported_2005} In addition to size-exclusion, it may be
+  possible to control the chemical environment within the nanopores by altering
+  the identities of the hydrophilic moieties that form the pores, affording
+  solute-specific separations.~\cite{dischinger_effect_2017}
 
@@
   Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
-  bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
+  bicontinuous cubic (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
   phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010}
-  When cross-linked, these materials can function as mechanically
-  strong separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
-  phase has hexagonally packed, straight pores which is the ideal geometry 
-  for high throughtput separations. However, the synthesis of H\textsubscript{II}
+  When cross-linked, these materials can function as mechanically strong
+  separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} phase
+  has hexagonally packed, straight pores which is the ideal geometry for high
+  throughtput separations. However, the synthesis of H\textsubscript{II}
   membranes with highly aligned hexagonal mesophases has been a challenge that
-  has been met with limited success and has prevented the material's viability 
-  as a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The Q\textsubscript{I} 
-  consists of a three dimensional network of tortuous and interconnected pores. 
-  It's more facile synthesis has yielded it more success. The latest 
-  Q\textsubscript{I} phase membranes have been shown to exhibit selectivities
-  higher than commercial NF and RO membranes permeabilities higher than commercial
-  RO membranes.~\cite{dischinger_application_2017}
+  has been met with limited success and has prevented the material's viability as
+  a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The
+  Q\textsubscript{I} phase consists of a three dimensional network of tortuous
+  and interconnected pores.  It's more facile synthesis has yielded it more
+  success. The latest Q\textsubscript{I} phase membranes have been shown to
+  exhibit selectivities higher than commercial NF and RO membranes with permeabilities
+  higher than commercial RO membranes.~\cite{dischinger_application_2017}
 
@@
 
+  % TODO: monomer structure
   Molecular dynamics (MD) simulations can give us mechanistic insights with
@@
   In this work, we present studies of the transport mechanisms exhibited by 20
-  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
-  character within the pores of an H\textsubscript{II} phase LLC. The pores of the 
-  H\textsubscript{II} phase have a similar topology to the Q\textsubscript{I} phase but
-  is a simpler geometry to model. In future studies, we will extend our techniques to
-  the Q\textsubscript{I} phase.
+  uncharged polar solutes with varying size, chemical functionality and
+  hydrophilic character within the pores of an H\textsubscript{II} phase LLC
+  membrane. The pores of the H\textsubscript{II} phase have a similar topology to
+  the Q\textsubscript{I} phase but their geomeitry is simpler to model. In future
+  studies, we will extend our techniques to the Q\textsubscript{I} phase.
 
@@
 
-  We first address the structure of the membrane nanopores. Previously, we
-  studied dry membrane systems and some systems with low water content. We showed
-  that those systems have rather crowded pores with high concentrations of monomer
-  head groups, sodium ions and water, where applicable. Here we build systems with
-  appreciable amounts of water, 5 and 10\% by weight, and analyze how the radial
-  density of monomer components and water change compared to our previous results.
+  We begin our analysis by studying the structure of the membrane nanopores.
+  Previously, we studied dry membrane systems and some systems with low water
+  content. We showed that those systems have rather crowded pores with high
+  concentrations of monomer head groups, sodium ions and water, where applicable.
+  Here we build systems with appreciable amounts of water, 5 and 10\% by weight,
+  and analyze how the radial density of monomer components and water change
+  compared to our previous results.
 
@@
   Python scripts used to set up systems and conduct post-simulation trajectory 
-  analysis (as described below and in the supporting information) are available 
-  online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. The 
+  analysis (as described below and in the Supporting Information) are available 
+  online at \\
+  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. The 
   appropriate scripts to use for the subsequent calculations are summarized in 
@@
   the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
-  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
-  We use GAFF as it has been used extensively for use with organic molecules.
-  We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
-  with QUACPAC from OpenEye Scientific Software.
+  Antechamber package \cite{wang_automatic_2006} shipped with
+  AmberTools16~\cite{case_ambertools16_2016}.  We use GAFF as it has been used
+  extensively with organic molecules.  We assigned atomic charges using the
+  am1bccsym method of \texttt{molcharge} included with QUACPAC from OpenEye
+  Scientific Software.
 
@@
 
-  Stable H\textsubscript{II} phases, assembled with Na-GA3C11, can be formed
+  Stable H\textsubscript{II} phases, assembled with monomer Na-GA3C11, can be formed
   using a broad range of water concentrations. In the literature, the system 
@@
   Information). We define the distal tail region to be ca. 1.5 nm from the pore
-  center based on the minimum in the radial distribution of water
+  center based on the minimum in the radial distribution function of water
   (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
@@
   insertion point we placed a randomly oriented solute molecule then ran a short 
-  energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
+  energy minimization. We allowed the solutes to equilibrate at 300K for 5 ns using Berendsen
   pressure control then collected transport data over the course of 1 $\mu$s MD simulations
@@
   For consistency with the presentation of our results, rather than calculate 
-  trends in $D$, we will calculate trends in trends in solute MSDs. For Brownian
+  trends in $D$, we will calculate trends in solute MSDs. For Brownian
   particles, $D$ is proportional to the MSD divided by time, $t$. Therefore, 
@@
   %BJC: another option is to fit to water which IS Brownian in the 10 wt% system.
-  In order to make qualitative comparisons, we fit Equation~\ref{eqn:msd-stokes-einstein}
-  so that it passed through the highest solute MSD. We assumed that the solute
-  with the highest MSD exhibited the closest to Brownian behavior and therefore could set
-  a rough boundary between subdiffusive, Brownian and superdiffusive MSDs. As a lower
-  bound to our appoximation, we also plotted the uncorrected version of 
-  Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the same 
-  value as the corrected curve for large radii. 
+  We fit Equation~\ref{eqn:msd-stokes-einstein} so that it passed through the
+  highest solute MSD. We assumed that the solute with the highest MSD exhibited
+  the closest to Brownian behavior and therefore could set a rough boundary
+  between subdiffusive, Brownian and superdiffusive MSDs. As a lower bound to our
+  appoximation, we also plotted the uncorrected version of
+  Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the
+  same value as the corrected curve for large radii. 
   % BJC: Set really high intersection value. Converges quickly (i.e. critical radius
@@
   \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
+  %TODO: reference for VMD
   package which allows us to directly check the validity of identified hydrogen bonds.
@@
   is due to a combination of the distal tail region's lower density (see 
-  Figure~\ref{fig:total_density})as well as oxygen atoms at the ends of each
+  Figure~\ref{fig:total_density}) as well as oxygen atoms at the ends of each
   monomer tail which can further stabilize water molecules.
@@
   \caption{Looking down at the $xy$ plane of the LLC membranes, the lowest density regions
-  of both membranes are in the pore center and in the tail region, furthest from the pore
+  of both membranes are in the pore center and in the distal tail region, furthest from the pore
   center (a \& c). Water is densest in the low density regions (b \& d).}\label{fig:total_density}
@@
   in the 5 wt\% water system. This behavior likely slows the motion of the 
-  sodium ions considerably compared to bulk water.
+  sodium ions considerably compared to in bulk water.
   %MRS2: is one sodium per carboxylate group correct?
@@
   Because the MSD of water in the pores of the 10 wt\% system is significantly
-  higher than that in the tails, we restrict our studies of transport in this paper to 
-  solutes in or near the pore center. Transport of solutes in the pores 
-  %MRS3:
-  %will 
-  is likely to be
-  be the 
-  limiting factor that determines permeability and rejection. Although tail transport of water in the 
-  the 5 wt\% water system is faster than pore transport, water transport overall is significantly slower
-  than in the 10 wt\% system. For practical applications, a membrane with water 
-  transport properties comparable to the 10 wt\% system is far more feasible than
-  the 5 wt\% system.
+  higher than that in the tails, we restrict our studies of transport in this
+  paper to solutes in or near the pore center. Transport of solutes in the pores
+  is likely to be the limiting factor that determines permeability and rejection.
+  Although tail transport of water in the the 5 wt\% water system is faster than
+  pore transport, water transport overall is significantly slower than in the 10
+  wt\% system. For practical applications, a membrane with water transport
+  properties comparable to the 10 wt\% system is far more feasible than the 5
+  wt\% system.
 
@@
   system (see Figures~\ref{fig:all_msds_5wt} and~\ref{fig:all_msds_10wt}). The fastest moving solute in both cases, 
-  methanol, has an MSD about 175 times larger in the 10 versus the 5 wt\%
+  methanol, has an MSD about 26 times larger in the 10 versus the 5 wt\%
   water system. Clearly the equilibrium water content of a given LLC system will 
@@
   %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
-
+  %TODO: add indication of scale
   \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
@@
 
-  The complex and non-homogeneous structure of the membrane leads to radially
+  The complex and inhomogeneous structure of the membrane leads to radially
   dependent transport mechanisms. In general, we observed that hops 
@@
   of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
-  head groups, 25\% go to the ether linkages connecting the monomers tails to the 
+  head groups, 25\% go to the ether linkages connecting the monomer tails to the 
   head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molecules in pores 
@@
   in all cases than that in the 10 wt\% water systems. The crowded pores of 
-  the 5 wt\% water system forces sodium ions in close proximity to solutes.
+  the 5 wt\% water system force sodium ions in close proximity to solutes.
 
@@
   than expected according to both the pure Stokes-Einstein relationship 
-  and the corrected relationship (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}).
+  and the corrected relationship (see Figure~\ref{fig:msd_radius_simple_alcohol_rdf}).
 
@@
   The order of the MSDs of the diols, triols and sugars are roughly consistent with 
-  their size; however, propylene glycol moves exceptionally slowly (see 
+  their size; however, propylene glycol moves exceptionally slow (see 
   Figure~\ref{fig:polyols_msd}). Ethylene glycol has the highest MSD followed
@@
   crystal monomer Na-GA3C11. We found that transport of solutes is 
-  %MRS3: tweak
-  %primarily
   governed by both water content as well as the interplay between the chemical functionality of the solute
   and the chemical functionality of the LLC monomer and ion making up the pore.
-  We 
-  %MRS3:
-  have shown
-  that the MSD of solutes, water and counter ions are highly 
+
+  We have shown that the MSD of solutes, water and counter ions are highly
   dependent on LLC membrane water content. As more water is added to the system,
-  the pores become 
-  %less crowded with monomer components. 
-  more dilute in the monomer components.
-  The MSDs of water and
-  sodium ions are nearly 2 orders of magnitude larger in the 10 wt\% system 
-  than in the 5 wt\% system. The amount of water in the pores 
-  %MRS3:
-  thus
-  deserves special
+  the pores become more dilute in the monomer components. The MSDs of water and
+  sodium ions are nearly 2 orders of magnitude larger in the 10 wt\% system than
+  in the 5 wt\% system. The amount of water in the pores thus deserves special
   attention when screening new monomers.
@@
   partition into the tail region as their hydrophobic tail increases in length.
-  Alcohols and sugars with multiple hydroxyl groups are very stable
-  in the pore region, but 
-  %frequent 
-  multiple
-  hydrogen bonds with monomer head 
-  groups prevent them from diffusing quickly. This effect is reduced when
-  hydroxyl groups are replaced with thiol groups, but the solutes become less
-  stable in the pore. Finally, solutes with carbonyl groups, which includes
-  the ketones, amides and solutes that can only accept hydrogen bonds, associate
-  with sodium ions, temporarily slowing or immobilizing them.
-
-  %MRS2: trying something else to emphasize what we are trying to do.
-Can you add a bit more detail so it's not just slowing up or speeding solutes, but slowing or speeding up solutes of a particular type?
-We can emphasize chemical selectivity .
-.
-.
-  %mitigate or enhance their effect on   solute MSDs.   
-  %BJC3: gave it a try. Broke into paragraphs
+  Alcohols and sugars with multiple hydroxyl groups are very stable in the pore
+  region, but multiple hydrogen bonds with monomer head groups prevent them from
+  diffusing quickly. This effect is reduced when hydroxyl groups are replaced
+  with thiol groups, but the solutes become less stable in the pore. Finally,
+  solutes with carbonyl groups, which includes the ketones, amides and solutes
+  that can only accept hydrogen bonds, associate with sodium ions, temporarily
+  slowing or immobilizing them.
+
   Based on these trapping mechanisms, we may be able to suggest modifications
-  that can be made to monomers that will modulate their effect on specific 
-  solute MSDs in order to make transport even more selective for particular 
-  solutes. Since solutes move slowly while entangled among the monomer tails,
-  and since more than half of the solutes studied spend at least 40\% of their
-  time in the tails, one can try to design monomers that better control the 
-  partition of solutes between the pore and tail region. Solutes move into 
-  the tails due both to their size and hydrophilic character. One may be 
-  able to contain solutes, even small ones like methanol, by increasing
-  the density of monomers close to the head groups through incorporation of 
-  cross-linkable groups in the vicinity. Alternatively, removal of the ether
-  linkages between the head groups and the monomer tails may decrease the 
-  stability of any of the molecules we studied near the head groups and 
-  force them to spend more time within the pore.
-
-  %Solutes that spend a large fraction of their 
-  %time in the tails, such as butanol with its high hydrophilic character, could
-  %exhibit higher permeabilities from these types of changes.
+  that can be made to monomers that will modulate their effect on specific solute
+  MSDs in order to make transport even more selective for particular solutes.
+  Since solutes move slowly while entangled among the monomer tails, and since
+  more than half of the solutes studied spend at least 40\% of their time in the
+  tails, one can try to design monomers that better control the partition of
+  solutes between the pore and tail region. Solutes move into the tails due both
+  to their size and hydrophilic character. One may be able to contain solutes,
+  even small ones like methanol, by increasing the density of monomers close to
+  the head groups through incorporation of cross-linkable groups in the vicinity.
+  Alternatively, removal of the ether linkages between the head groups and the
+  monomer tails may decrease the stability of any of the molecules we studied
+  near the head groups and force them to spend more time within the pore.
 
@@
   carbonyl-containing solutes like urea for longer periods of time. Of course,
-  an increased valence would require proportionately less total counter ions
+  an increased valence would require proportionately less total counterions
   to balance the system charge which could result in the opposite effect. One
@@
   which may eliminate their interaction with most solutes.
-
-%  
-%  These hypotheses remain to be tested in future simulations of new
-%  monomers.
 

### 2019-05-08 Ben_Manuscripts/transport/Draft.tex
Minor figure changes

@@
 \usepackage{amssymb}
-\usepackage{array}
+%\usepackage{array}
 \usepackage{siunitx}
@@
 \newcommand{\angstrom}{\textup{\AA}}
-\newcommand{\colormap}{jet}  % colorbar to use
+%\newcommand{\colormap}{jet}  % colorbar to use
 \usepackage{cleveref}
@@
 \usepackage{xr}
+\usepackage{multicol}
 \usepackage{tcolorbox}
-\usepackage{multicol}
 
@@
 
-  % TODO: monomer structure
   Molecular dynamics (MD) simulations can give us mechanistic insights with
@@
   formed by the monomer Na-GA3C11, expanding upon the most recent experimental
-  characterization.~\cite{coscia_understanding_2018,feng_thin_2016} We developed
+  characterization.~\cite{coscia_understanding_2019,feng_thin_2016} We developed
   techniques to simulate the hexagonal phase formed by neat monomer as well as
@@
   membrane. The pores of the H\textsubscript{II} phase have a similar topology to
-  the Q\textsubscript{I} phase but their geomeitry is simpler to model. In future
+  the Q\textsubscript{I} phase but their geometry is simpler to model. In future
   studies, we will extend our techniques to the Q\textsubscript{I} phase.
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
+  \vspace{1.4cm}
+  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
+  \vspace{1cm}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{ortho_view.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{top_view.pdf}
@@
   %BJC3: gave it another shot
-  \caption{The H\textsubscript{II} phase formed by LLC monomers consists of pores
-  that are approximately straight (a) and packed hexagonally (b). In both figures,
-  water molecules that occupy the pores are colored blue, the hydrophilic head 
-  groups of the LLC monomers are colored orange and all else is colored gray. 
+  \caption{The H\textsubscript{II} phase formed by LLC monomer NaGA3C11 (a)
+  consists of pores that are approximately straight (b) and packed hexagonally (c).
+  In both figures, water molecules that occupy the pores are colored blue, 
+  the hydrophilic head groups of the LLC monomers are colored orange and all else is colored gray. 
   The chemical environment within the nanopores is largely determined by the functionality
@@
   \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
-  %TODO: reference for VMD
-  package which allows us to directly check the validity of identified hydrogen bonds.
-  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
-  show that our conclusions are insensitive to this definition within a 
-  reasonable range of distances and angles.
+  package which allows us to directly check the validity of identified hydrogen 
+  bonds~\cite{humphrey_VMD:_1996}. In Section~\ref{S-section:hbond_sensitivity} 
+  of the Supporting Information, we show that our conclusions are insensitive
+  to this definition within a reasonable range of distances and angles.
 
@@
   \end{subfigure}
-  \caption{Looking down at the $xy$ plane of the LLC membranes, the lowest density regions
-  of both membranes are in the pore center and in the distal tail region, furthest from the pore
-  center (a \& c). Water is densest in the low density regions (b \& d).}\label{fig:total_density}
+  \caption{Looking down at the $xy$ plane of the cross-linked LLC membranes, the lowest
+  density regions of both membranes are in the pore center and in the distal tail region,
+  furthest from the pore center (a \& c). Water concentration is highest in regions of
+  low monomer density regions (b \& d).}\label{fig:total_density}
   \end{figure}
@@
   %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
-  %TODO: add indication of scale
   \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly

### 2019-05-08 Ben_Manuscripts/transport/cover_letter.tex
Minor figure changes

@@
         liquid crystal (LLC) polymer membrane. This is one of the
-        first, and far the most extensive, uses of molecular dynamics
-        to understand the molecular details of transport in such
-        chemical complex nanostructured channels. Most importantly, we
+        first, and by far the most extensive, uses of molecular dynamics
+        to understand the molecular details of solute transport in such
+        chemically complex nanostructured channels. Most importantly, we
         show how such channels can give rise to selective transport
@@
 
-		\item Eric Jankowski has experience modeling soft materials using molecular dynamics
-		including work done simulating structure factors from simulations, much like
-		the techniques we use in our work (Boise State University, 208-426-5681,
-		\href{mailto:ericjankowski@boisestate.edu}{ericjankowski@boisestate.edu})
+		\item Mahesh Mahanthappa has experience modeling soft materials using molecular dynamics
+		including work on ion transport in various ordered liquid crystalline phases. 
+		(University of Minnesota, 612-625-4599,\href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})
 

### 2019-05-08 Ben_Manuscripts/transport/figures/msd_bar_chart.py

@@ -10,7 +10,7 @@ crsr = connection.cursor()
 restrict_by_name = False 
 MW = False  # plot mw of species
 penalty = 0.25
-wt = 5 
+wt = 10
 
 group = 'all'
 
@@ -111,6 +111,9 @@ if MW:
 	ax1.bar(index + bar_width, mw, bar_width, alpha=opacity, label = 'Molecular Weight', color='red')
 	ax1.tick_params(labelsize=14)
 	ax1.set_ylabel('Molecular Weight (g/mol)', fontsize=14)
+
+if wt == 10:
+	plt.text(1.25, 3.25, '*Scale is 25x part (a)', fontsize=14)
 
 plt.xlim(-0.2, len(labels))
 fig.tight_layout()

### 2019-05-13 Ben_Manuscripts/comps/Draft.tex
Added draft

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage[x11names,table]{xcolor}
\usepackage{setspace}
\usepackage[font=small]{caption}
\setstretch{1.5} % line spacing
\captionsetup[table]{font={stretch=1,small}} % line spacing in tables
\captionsetup[figure]{font={stretch=1,small}} % line spacing in figures
\usepackage{url}
% For timeline
\newcommand{\foo}{\color{LightSteelBlue3}\makebox[0pt]{\textbullet}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}
\DeclareCaptionFont{blue}{\color{LightSteelBlue3}}
\usepackage{array,booktabs}
\usepackage[superscript,biblabel]{cite}  % make citations superscripts to save space
%\setlength{\belowcaptionskip}{-1.2\baselineskip}

\title{PhD Research Proposal: Molecular Level Design of Nanoporous Lyotropic Liquid
Crystal Membranes for Aqueous Separations \\ \vspace{0.5cm}
\large Advisors: Michael Shirts and Richard Noble}

%MRS: overall, really nice start.  You can cut back a little on the detail and emphasize a bit more ``This is what the data means and what the consequnces are.  Need to flesh out objective 3 a more (and objective 4 a bit more). 
\author{Benjamin J. Coscia}

\begin{document}

  \graphicspath{{./figures/}}

  \maketitle
  \thispagestyle{empty}
  \clearpage
  \setcounter{page}{1} % don't count title page as a page

  \section{State of the Art}\label{section:state-of-the-art}

  \subsection*{Commercial Membranes for Small Molecule Separations}

  % perhaps a word or two about micro and ultra filtration

  %MRS: probably can do a little less introduction of the overall membrane needs, as we want to make sure 
  %MRS: the focus is on the research (thesis, you can include everything).  Can probably hold off that until you get the rest done, then trim as needed for space.
  %
  %MRS: remember the purpose of the introduction to any document is to lay out the rules of engagement; you want 
  %MRS: to raise the questions that the rest of the document will answer.
  % 
  %MRS: try to make sure the application motivation and the research described match up when possible.
  %MRS: if particular applications wouldn't be directly enabled by the research, at least draw to the connection
  %MRS: i.e. talk about the general tools of computation to understand nanostructured membranes, even if the current
  %MRS: membranes under development aren't suitable for the particular separations described.
  %BJC: Something like: The computational techniques developed here are suitable not just for LLC Membranes, but for any nanostructured 
  % membrane material.

  More highly selective nanoporous membranes would be useful for 
  performing complex aqueous separations with seawater and various
  types of wastewater. For example, sodium chloride and boron in seawater 
  \cite{fritzmann_state---art_2007} and organic micropollutants found in
  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
  represent a small subset of the diverse contaminants of water sources. 
  By efficiently separating contaminants from feed solutions with
  highly selective membranes, it is possible to reduce the number of 
  required membrane passes and post-treatment steps needed for a given 
  filtration process \cite{werber_materials_2016}, thus lowering energy 
  requirements and cost. Additionally, one can extract valuable 
  resources from the feed streams. For example, flowback water produced 
  during hydraulic fracturing of shale formations contains dissolved 
  species like acetate whose extraction has economic value \cite{dischinger_application_2017}.

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing commercial membrane
  filtration processes that can be used to separate solutes on the order of
  1 nm in size and smaller, including ions. Both apply hydraulic pressure 
  to the feed solution in order to overcome osmotic pressure and force water
  and unfiltered components through the membrane. RO membranes are typically
  thin film composite with a porous mechanical support layer and a thin but
  dense polymer matrix active layer where separations occur.\cite{jeong_interfacial_2007}
  RO separates solutes based on the solute's ability to dissolve into and 
  diffuse through the tortuous pathways available in the membrane's dense 
  active layer. RO offers high selectivity at the cost of relatively high 
  energy requirements since one must apply hydraulic pressure on the order of
  50--100 bar to the feed solution in order to achieve an economical flux~\cite{van_der_bruggen_review_2003}.
  In contrast to RO membranes, NF membranes have explicit pores on the order
  of 1 nm in size. Typically, separations are achieved based on size exclusion
  and Donnan exclusion if the membrane's surface has a net charge.~\cite{donnan_theory_1995}
  NF membranes require significantly less applied pressure in order to achieve solute flux
  comparable to RO. Unfortunately, conventional NF membrane synthesis processes, such as 
  phase-inversion\cite{smolders_microstructures_1992}, are stochastic in
  nature which yields pores that are polydisperse in size.\cite{werber_materials_2016}
  Pore size polydispersity is detrimental to membrane selectivity.

  The downfall of RO and NF membranes can be summarized by the well-known
  permeability-selectivity tradeoff. Namely, it is difficult to increase the
  permeability of a desired molecular or atomic species, while maintaining
  the same retention of an undesired species.\cite{werber_materials_2016}

  \subsection*{Nanostructured Membranes}

  Nanostructured membranes attempt to overcome the permeability-selectivity 
  tradeoff through intelligent design at the molecular level. Graphene sheets, 
  carbon nanotubes (CNTs) and zeolites are three highly studied nanostructured
  technologies.

  Ultrathin-film graphene and graphene oxide membranes are a very active
  area of research because they offer potential for extremely high 
  permeability membranes. An ideal graphene membrane is a 2D material 
  composed of a single layer of graphene.\cite{humplik_nanostructured_2011}
  Synthesis of a single layer of graphene at a large scale without introducing
  defects is a challenge that has not yet been overcome. Multilayered graphene
  membranes are potentially easier to synthesize and more scalable which has 
  resulted in an increasing interest over recent years.\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}

  Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001} 
  Practically, dispersing CNTs into a polymer matrix is extremely difficult
  because they tend to agglomerate due to Van der Waals forces. Functionalization
  of the CNT walls has been heavily investigated  as a way to overcome this issue, however 
  alignment of the CNTs into an array feasible as a nanoporous membrane 
  persists as a challenge to CNT membranes.\cite{sahoo_polymer_2010}

  Zeolite-coated ceramic membranes offer the potential for permeabilities
  comparable to ultrafiltration, molecular sieves with pores up to 100 nm in 
  size~\cite{werber_materials_2016}, with selectivities as good as NF and RO. 
  Zeolites have highly uniform nm-sized crystalline structures with cage-like
  cavities that allow movement and trapping of small solutes. The crystalline
  frameworks are typically formed by networks of silicon and aluminum each 
  attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
  One can replace the silicon and aluminum atoms via ion exchange in order to
  control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}
  A number of studies have tested the permeability and sodium salt rejection
  of various zeolite membranes, however none have fully overcome the 
  permeability-selectivity tradeoff.~\cite{pendergast_review_2011}
%    \item Most are prone to defects in the crystalline structure.

  \subsection*{Lyotropic Liquid Crystal Membranes}

  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
  (LLC) membranes can be produced at moderate scale and may be capable of 
  performing highly selective separations. LLCs are amphiphilic molecules 
  that have the ability to self-assemble into porous nanostructures~\cite{smith_ordered_1997}
  that can be cross-linked to create mechanically strong membrane films with 
  periodic uniform-sized pores on the order of 1 nm in diameter~\cite{zhou_supported_2005}. 
  Since LLC polymer membranes lack an appreciable pore size distribution, they 
  inherently exhibit high selectivity due to their molecular weight cut-off 
  (MWCO)~\cite{zhou_supported_2005}. Additionally, LLC monomers can be salts,
  and therefore lead to Donnan exclusion of ions at the membrane-feed solution 
  interface.\cite{donnan_theory_1995}
%    The membrane gains a net surface charge when counterions from
%  the head groups that line the pore walls escape into the feed solution in an
%  effort to balance the gradients of concentration and electric potential
%  \cite{donnan_theory_1995}.

  % BJC: should show figure with HII and QI monomer structures
  The feasibility of nanostructured LLC polymer membranes for selective separations
  has been demonstrated using LLC monomers that form the type 1 bicontinuous cubic
  (Q\textsubscript{I})~\cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
  and the inverted hexagonal (H\textsubscript{II}) 
  phases (see Figure~\ref{fig:structures}).~\cite{zhou_supported_2005} When separating organic solutes from NaCl, Q\textsubscript{I}-phase
  membrane filtration experiments have shown selectivity 2--3 times higher than
  commercial RO and 6--12 times higher than commercial NF membranes.~\cite{dischinger_application_2017}
  When separating a series of various sized dyes, an H\textsubscript{II}-phase 
  LLC membrane showed complete rejection of dyes bigger than 1.2 nm in size~\cite{zhou_supported_2005}.

%  \begin{wrapfigure}{L}{0.5\textwidth}
%  \centering
%  \includegraphics[width=\linewidth]{NaGA3C11_colorcoded.eps}
%  \includegraphics[width=0.8\linewidth]{q1_monomer.png}
%  \end{wrapfigure}

%  \begin{wrapfigure}{L}{0.75\textwidth}
  \begin{figure}
  \centering
  \begin{subfigure}{0.55\linewidth}
  \hspace{0.5cm}
  \includegraphics[width=0.8\linewidth]{NaGA3C11_colorcoded.eps}
  \vspace{1.4cm}
  \caption{}\label{fig:HII_mon}
  \end{subfigure}
  \begin{subfigure}{0.4\linewidth}
  \hspace{0.4cm}
  \includegraphics[width=0.7\linewidth]{q1_monomer.png}
  \caption{}\label{fig:q1_mon}
  \end{subfigure}
  \caption{H\textsubscript{II} and Q\textsubscript{I} phase LLC membranes have 
  been synthesized from monomers in (a) and (b) respectively. One can 
  alter membrane properties by modifying the length and number of tails (red), the
  functional head group (green) and the counterion identity (blue) of LLC monomers.}\label{fig:structures}
  \end{figure}

  Q\textsubscript{I}-phase membranes consist of a tortuous network of three
  dimensionally interconnected pores that prevent optimal through-plane
  transport. In contrast, the densely packed, non-tortuous and uniform sized
  pores of H\textsubscript{II}-phase membranes represent the ideal geometry
  for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}. However,
  the hexagonally packed LC domains of the H\textsubscript{II}-phase are generally
  unaligned, which hurts membrane permeability. This domain scale misalignment
  had inhibited further development of this technology, and research efforts were
  focused on the Q\textsubscript{I} phase, whose geometry does not require 
  alignment~\cite{zhou_new_2007}.

%  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:assembly}) has a
%  high theoretical capacity for transport than the Q\textsubscript{I} phase.
%  \begin{itemize}
%	  \item The H\textsubscript{II} phase forms at room temperature in the 
%	  presence of ca.~10 wt\% water and consists of hexagonally packed, 
%	  hydrophilic pore columns\cite{smith_ordered_1997}. 
%%	  \item The hexagonal, straight-pore geometry provides a dense array
%%	  of hydrophilic channels and short pathways for solutes to travel.
%	  % BJC: should rethink the following since we think that thermotropic doesn't exist
%	  \item In the absence of water, neat monomer will form the same hexagonal
%	  columnar structure which, in the literature, has been referred to as the
%	  Col\textsubscript{h} thermotropic phase\cite{feng_scalable_2014}.
%  \end{itemize}

  Recently, researchers learned how to macroscopically align the hexagonal 
  domains which has revived research into H\textsubscript{II}-phase LLC
  polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
  domains, a temperature-dependent hexagonal phase created by neat LLC monomers,
  using a magnetic field with subsequent cross-linking to lock the structure 
  in place\cite{feng_scalable_2014}. In 2016, Feng et al.~showed that one could 
  also obtain the same result by confining the neat monomer between PDMS or glass 
  substrates since hexagonal mesophases preferentially anchor perpendicular to 
  both surfaces\cite{feng_thin_2016}.

  Unfortunately, reproducing the work of Feng et al. with the hydrated 
  H\textsubscript{II} phase has been an experimental challenge. Therefore, the
  primary focus of experimental research efforts has been with the Q\textsubscript{I} 
  phase.

  \section{Project Objectives}\label{section:objectives}

  Our current understanding of the molecular details of LLC membranes'
  nanostructure is not sufficient to be able to precisely design them for
  specific separations. Dischinger et al.~attempted to use an empirical model
  that correlates the physicochemical properties of the counterion used in
  a Q\textsubscript{I}-phase LLC membrane to solute rejection. Although there
  was some agreement with their empirical model, it does not offer a 
  sufficiently detailed explanation of the critical molecular interactions 
  leading to the observed behavior.~\cite{dischinger_effect_2017} 
  H\textsubscript{II}-phase LLC polymer membrane studies have been limited
  primarily to the Na-GA3C11 monomer (Figure~\ref{fig:HII_mon}) with
  some characterization done after minor monomer structural modifications. 
  These studies emphasized large scale structural features such as pore spacing
  as well as size-based rejection.~\cite{zhou_supported_2005,resel_structural_2000}
  Given the similar topology of H\textsubscript{II} and Q\textsubscript{I}
  membrane pores, we expect the H\textsubscript{II} phase will also be 
  subject to complex solute-membrane interactions that are not easily explained
  by an empirical model.

  A molecular-level understanding of structure and transport in LLC polymer 
  membranes, enabled by molecular dynamics (MD) simulations, can provide 
  guidelines to reduce the large chemical space available to design
  monomers for creation of separation-specific membranes. Using a sufficiently
  accurate molecular model, we can observe transport of solutes within LLC 
  membrane nanopores with atomistic resolution and infer mechanisms. 
  Based on this information we will have a much greater capability to 
  intelligently design new membranes by screening new liquid crystal monomer
  designs with MD simulations. The principles learned can be implemented 
  and tested experimentally.

  \noindent There are four primary objectives of this PhD research.
  \begin{enumerate}

    \item Develop techniques to build and understand the nanoscopic structure
    of LLC membranes.

    %MRS: probably should talk about this 1) with proper tense (some of these things have been done) and 2) talk about what YOU are doing, not we. I helped design the research, but you carried essentially all of it out! If phrased in future tense, committee will be confused, thinking those are things still to be done.

    A useful molecular-level model should incorporate a detailed picture 
    of the nanoscopic pore structure, which is crucial to understanding
    the role of monomer structure in solute transport and membrane design.
    I have created a maximally consistent structural model by comparing 
    simulated X-ray diffraction (XRD) patterns, generated from MD trajectories,
    to an experimental 2D wide angle X-ray scattering (WAXS) spectrum of a 
    Col\textsubscript{h} phase LLC membrane. I have used this model as an 
    example in order to understand the ease with which we can apply our approach
    to alternate monomers and other LC phases.

%    shown that we achieve a
%    similar pore composition regardless of initial configuration which is 
%    influenced by a number of variables. This implies that our model can
%    
%        We will assess the extent to which
%    we can apply our understanding to the H\textsubscript{II} phase, as well
%    as systems built with alternate monomers.

    \item Determine dominant solute-membrane interactions that give rise to
    transport mechanisms.

    I observed the transport of a relatively large set of small polar solutes
    placed within the H\textsubscript{II} phase membrane nanopores. I analyzed
    the time series of each solute's position in addition to directly measuring
    the physical interactions, such as hydrogen bonding and ion coordination, 
    between solutes and LLC monomers.

    \item Create a stochastic model which can project long timescale 
    transport behavior.

    I will combine my qualitative knowledge of the solute transport mechanisms
    with simulation data in order to inform a stochastic model. This model
    should closely reproduce the properties of the time series that we observe 
    in our simulations. Due to the low computational cost of a stochastic model
    relative to MD simulations, I will be able to forecast long timescale transport
    behavior and make well-converged predictions of macroscopic transport properties.

    \item Adapt the same analysis to the Q\textsubscript{I} phase.

    Over the course of this project, experimental research surrounding
    LLC membranes has shifted nearly all focus towards the Q\textsubscript{I}
    phase due to its more facile synthesis.	Although most of my work has 
    been applied to the H\textsubscript{II} phase, much of the same analyses
    can be applied to the Q\textsubscript{I} phase. The biggest challenge will
    be adapting my techniques to its more complex three dimensional geometry.

%    \item Enable easy continuation of our work with a dedicated and 
%    well-documented python package.
%    
%	Although molecular simulations have become popular
%	for studying systems at the atomic level, LLCs used in this context
%	have not been heavily investigated. Consequently, much of the 
%	analysis developed for this project is not widely applied. Therefore, 
%	it is important for us to make available the scripts that reproduce
%	the exact results presented in our published papers along with detailed
%	documentation of the scripts. This will ensure near-seamless continuation
%	of this project and accelerate the development of LLC membranes.

  \end{enumerate}

%MRS: overall, good description of wha has been done.  You can cut back a little if space is an issue.  Give the paper citations with the points. 
  \section{Progress to Date}\label{section:progress}

  \textbf{\large Objective 1:} {\large Build and understand the nanoscopic structure
  of the H\textsubscript{II} phase} (\textcolor{green!40!olive}{\textbf{Complete}})

  My first task was to develop a procedure for building and equilibrating 
  an atomistic LLC membrane system (see Figure~\ref{fig:assembly}). I chose to build
  a monoclinic unit cell consisting of four pores. Each pore is composed of monomer
  columns, where each column consists of 20 monomers stacked on top of each other
  so that the phenyl groups are coplanar with each other and the $xy$ plane. The
  columns are oriented so that the hydrophilic monomer head groups face towards
  the pore center. I did not add any water to the initial configuration because I
  compared the structure to experimental data for a system claimed to be
  synthesized with only neat monomer. I equilibrated unit cells using a series
  of simulations with head groups held in place by position restraints, gradually
  reducing the force constant of the position restraints until the system
  was completely unrestrained. I let the system equilibrate for 400 ns of simulation
  time.

  \begin{figure}[!htb]
      \centering
      \begin{subfigure}{.325\textwidth}
              \centering
              \vspace{0.5cm}
              \includegraphics[width=\textwidth]{NaGA3C11_wedge.eps}
              \vspace{0.05cm}
              \caption{}~\label{fig:monomer}
      \end{subfigure}
%      \begin{subfigure}{.3\textwidth}
%              \centering
%              \includegraphics[width=\textwidth]{monomer_twocolor.pdf}
%              \caption{}~\label{fig:atomistic_monomer}
%      \end{subfigure}
%      \begin{subfigure}{0.3\linewidth}
%              \centering
%              \includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
%              \caption{}~\label{fig:wedge}
%      \end{subfigure}
              \begin{subfigure}{0.325\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{columns.pdf}
              \caption{}~\label{fig:wedge_layer}
      \end{subfigure}
      \begin{subfigure}{0.325\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
              \caption{}~\label{fig:hex_packing_simple}
      \end{subfigure}
      \caption{(a) The LLC monomer Na-GA3C11 exhibits wedge-like character. (b) 
      Monomers stack on top of each other to create columns with short range order,
      then assemble into pores with hydrophilic head groups (blue) facing towards 
      the pore center. (c) The pores assemble into hexagonally packed columnar
      mesophases.}~\label{fig:assembly}
      \vspace{-0.5cm}
  \end{figure}

  I evaluated a number of different initial column architectures. I stacked 
  monomers in parallel displaced and sandwiched configurations, two possible
  $\pi$-$\pi$ stacking modes.\cite{sinnokrot_estimates_2002} I also varied 
  the initial distance between stacked monomers, $d$. I chose $d$ values of 
  3.7~\AA, based on experimental WAXS measurements, as well as 5 \AA~as a 
  test of its sensitivity.

  My model's geometry is most consistent with experiment for systems built
  with 5 columns per pore and monomers initially stacked 3.7 \AA~apart
  (see Figure~\ref{fig:p2p}). I equilibrated systems with 4, 5, 6, 7 and 
  8 columns per pore. The pore spacing of 5 column-per-pore systems agree
  well with experiment. 6 column-per-pore systems built with $d$ = 5 \AA~appear
  to yield an experimentally consistent pore spacing however, the equilibrated
  distance between stacked monomers stay close to 5 \AA~which is inconsistent
  with experiment. In general, the equilibrated distance between monomers stays
  close to its initial value.

  \begin{wrapfigure}{L!}{0.5\textwidth}
    \centering
    \vspace{-0.5cm}
    \includegraphics[width=\linewidth]{p2p.pdf}
    \caption{Systems with 5 columns per pore have equilibrated pore spacings
            closest to the experimental value of 4.12 nm. The equilibrated 
            pore spacing of the model increases as the number of columns in
            each pore increases.}~\label{fig:p2p}
    \vspace{-1.75cm}
  \end{wrapfigure}

%  \noindent On timescales that we can reasonably simulate, our equilibrated
%  structures show some initial configuration dependence. 
%  \begin{itemize}
%    \item All of the systems used to generate Figure~\ref{fig:p2p} are at 
%    least metastable.
%    \item We observe no large scale rearrangements that would be necessary
%    for all structures to converge to the same equilibrium structure. 
%  \end{itemize}

  I further validated the structure of our molecular model by verifying 
  its consistency with five major reflections present in the experimental
  WAXS pattern. Using MD trajectories, we simulated X-ray diffraction (XRD)
  patterns that we could compare to the WAXS data by taking the appropriate
  cross-section of the time-averaged 3D structure factor. The five major 
  reflections and the structural features leading to them are summarized
  and described in the caption of Figure~\ref{fig:WAXS_comparison}. None of
  the models simulated to this point could reproduce R-double.

  It is necessary to add a small amount of water to the model in order to 
  fully reproduce all features of the WAXS pattern (see Figure~\ref{fig:solvated_XRD}).
  I obtain the most experimentally consistent structure when I build systems
  in the parallel displaced configuration with 1 wt\% water added to the pores. 
  This is the only configuration that gives rise to the R-double feature. R-double
  appears because vertically adjacent monomer head groups hydrogen bond with shared 
  water molecules, causing them to be drawn closer together. When multiple 
  pairing interactions occur in series along the same pore axis, the center
  of masses of the pairs are spaced apart at twice the $\pi$-stacking distance. 
  The necessity of water in my model suggests that the membrane synthesized by
  Feng et al. was slightly hydrated due to water molecules leached from 
  surroundings by the hydroscopic monomers. Similar suspicions have been voiced
  by experimentalists in unpublished communications.

  \begin{wrapfigure}{R!}{0.65\textwidth}
  	\centering
  	\vspace{-0.5cm}
    \begin{subfigure}{0.49\linewidth}
    	\includegraphics[width=\linewidth]{WAXS_annotated_words.pdf}
        \caption{Experiment}\label{fig:WAXS}
    \end{subfigure}
	\begin{subfigure}{0.49\linewidth}
        \includegraphics[width=\linewidth]{solvated_offset_rzplot_1.pdf}
        \caption{Simulation}\label{fig:solvated_XRD}   
	\end{subfigure}
    \caption{(a) 2D-WAXS gives details about repeating features on the order of
    angstroms. Explanations for each of the 5 major reflections present are
    as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack 3.7 \AA~apart. 
    (R-double) Monomer head groups associate into pairs by hydrogen bonding with
    a shared water molecule. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. 
    (R-spots) Monomer tails pack hexagonally. (R-pores) The pores are spaced 
    4.12 nm apart and pack hexagonally. (b) We obtain a maximally consistent
    match between simulated XRD patterns and experimental WAXS data when we
    build systems in the parallel displaced configuration with 1 wt \% water
    included in the pores.}\label{fig:WAXS_comparison}
    \vspace{-0.75cm}
 \end{wrapfigure}

  %BJC: I think this is important to say somewhere
  %BJC: but I don't have an ensemble of 1 wt % systems to fully prove that with.
  %BJC: I could show cross-sections of R-pi, but that would require more context. 
  On the timescales that we can reasonably simulate, our model exhibits slow 
  dynamics. Consequently, there are very few uncorrelated frames in our 
  trajectories which leads to noise and sharpened reflections in the simulated
  XRD patterns. We can overcome this issue by combining the structure factors
  generated from an ensemble of trajectories produced starting from an ensemble
  of uncorrelated initial configurations.

  The composition of the pores does not change regardless of which
  initial configuration we study. In Figure~\ref{fig:overlaid_densities}, we 
  plot the radial density of various monomer components as a function of distance
  from the pore centers. All are qualitatively similar meaning that a solute 
  placed in any of these systems should experience a similar chemical environment.
  Although we will move forward with our most promising configuration, this is 
  an important finding since it implies that we do not need to apply the same level
  of rigor when screening new monomers.

  My work towards this objective is published in the Journal of Physical Chemistry B:
  Coscia et al. \textit{J. Phys. Chem. B}, 123, 289-309 (2019).

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  %BJC: probably change this legend to `d = x Angstroms` instead of 
  % disordered/ordered, since I don't have space to talk about ordered / disorderd configurations (requires 
  % nematic order parameter to give a complete justification of the names)
  \includegraphics[width=\textwidth]{regional_density_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.pdf}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.pdf}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.pdf}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  \caption{In all systems studied, the component radial distribution functions are similar.
      They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
          regions. The biggest differences are at r=0 where noise is higher due to
          decreased sampling. The center of the pore is not hollow, but contains sodium ions and
          head groups, even when the system is solvated. This architecture may impede transport in
          the real system in a chemically-dependent manner.
          The solvated system has a lower density of head groups near the
          pore center which is likely due to the swelling that is necessary in order to fit water
          molecules in the pore region.}~\label{fig:overlaid_densities}
  \vspace{-0.5cm}
  \end{figure}

  \noindent \textbf{\large Objective 2:} \textit{\large Determine transport mechanisms} (\textcolor{green!40!olive}{\textbf{Complete}})

  We added additional water to our most experimentally consistent structural
  model in order to create a higher water content H\textsubscript{II} phase
  model. Researchers have synthesized the H\textsubscript{II} phase using 
  the NaGA3C11 monomer with water contents ranging from 7 - 20 wt\%, with 
  10 wt\% being the most common.~\cite{smith_ordered_1997,zhou_supported_2005} 
  However, Resel et al. stated that the system is likely fully hydrated at
  7 wt \% water with additional water trapped in defects between mesophases.~\cite{resel_structural_2000}
  Consequently, we chose to build two systems with 5 and 10 wt\% water.

  \begin{wrapfigure}{l}{0.65\textwidth}
  \centering
  \vspace{-0.4cm}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{component_density_dry.pdf}
%  %BJC: simulation is extended to smooth out these curves
%  \caption{Dry System}\label{fig:component_density_dry}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \vspace{-0.5cm}
%  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
%  \label{fig:monomer_color_coded}
%  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to
  the color-coded monomer pictured in Figure~\ref{fig:HII_mon}. All RDFs
  represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin to which they belong. The black
  dashed lines are positioned so that they intersect with the maximum head group
  density. (a) In the 5 wt \% system, monomer head groups are situated about 0.45 nm
  from the pore center. Sodium and water are densest near the pore center 
  (b) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
  for more water. Water is densest at the pore center, but sodium ion density
  peaks closer to the head groups since many stay bound to carboxylate groups.}\label{fig:component_densities}
  \vspace{-0.75cm}
  \end{wrapfigure}

  Upon simulating each system, we observed that water partitions into the
  distal tail region. Based on the radial distance from the pore center where 
  the minimum water density occurs, we defined the distal tail region to 
  be greater than 1.5 nm from any pore center. There
  is approximately a 3:2 ratio of water in the pores to water in the 
  distal tails. Due to the wedge shape of the monomers, the distal tail
  region has a relatively low density leaving space for water molecules 
  to fill.

  The pores of the H\textsubscript{II} phase are primarily a mixture of 
  water and sodium ions. The maximum density of head groups occurs 0.45
  and 0.65 nm from the pore center in the 5 and 10 wt\% water systems 
  respectively (see Figure~\ref{fig:component_densities}). There are 
  almost no head groups occupying the pore center.

  Water and sodium transport is significantly faster in the less crowded 
  10 wt\% water pores. The mean squared displacement (MSD) of water is about
  51 times higher and the MSD of sodium is about 49 times higher compared to
  the 5 wt\% system. In general we observe similar solute transport mechanisms
  in the 5 and 10 wt\% water systems but on different time scales.
    %BJC: might as well leave 5 wt% data in there.
%    \item Therefore, we focus the remainder of this discussion on the 10 wt\%
%    water system since we were able to collect a larger quantity of mechanistic
%    data from the solute trajectories.

  % BJC: do you think I can get away with an appendix with the solute table + abbreviations that
  % doesn't count towards the page limit?
  We observed transport of 20 different small polar solutes in the pores of
  our model. We created a separate initial configuration for each solute 
  studied and placed 6 solutes, equally spaced in $z$, in each nanopore.
  After a 5 ns equilibration, we allowed the solutes to simulate for
  1 microsecond.

  \begin{figure}
  \includegraphics[width=\textwidth]{solute_table.pdf}
  \caption{The solutes studied in this work along with the abbreviations used
  in subsequent figures and their chemical structures. Solutes are color-coded
  according to similarities in their structure. Blue corresponds to simple 
  alcohols, red to diols, triols and sugars, green to ketone-like solutes, 
  orange to sulfur-containing solutes and yellow to solutes that can only accept
  hydrogen bonds but not donate.}\label{fig:solute_table}
  \vspace{-0.5cm}
  \end{figure}

%  \begin{wrapfigure}{R}{0.6\textwidth}
%  \centering
%  \begin{subfigure}{0.45\linewidth}
%  \includegraphics[width=\linewidth]{all_10wt_tamsds.pdf}
%  \caption{10 wt \% water}\label{fig:all_msds_10wt}
%  \end{subfigure}
%  \begin{subfigure}{0.45\linewidth}
%  \includegraphics[width=\linewidth]{msd_radius_10wt.pdf}
%  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
%  \end{subfigure}
%  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
%  smaller than those of the solutes in the 10 wt \% water system (b). The
%  MSDs are not a monotonic function of molecular size (c and d). A significant
%  number of solute MSDs fall below the theoretical lines predicted by the
%  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
%  }\label{fig:msds}
%  \vspace{-1.5cm}
%  \end{wrapfigure}

  The solute MSDs are not a monotonic function of solute size. In 
  Figures~\ref{fig:all_msds_5wt} and~\ref{fig:all_msds_10wt}, we plot
  the average MSD of each solute. In Figure~\ref{fig:msd_radius_5wt} 
  and~\ref{fig:msd_radius_10wt}, we plot solute MSDs against their
  molecular radius. We also show theoretical curves which illustrate the 
  expected MSD of each solute if they were to travel unhindered. We 
  ensured that the Stokes-Einstein equation with the correction factor
  of Gierer and Wirtz\cite{gierer_molekulare_1953} passed through methanol's MSD and radius
  in order to give an approximate frame of reference. The correction 
  factor attempts to include the effects of microfriction that begin to 
  play a role when solute size becomes on the order of solvent size. 
  Since methanol is small, we assume that it travels unhindered relative 
  to all other solutes. The theoretical line serves as an approximate 
  boundary between subdiffusive, Brownian and superdiffusive behavior.
  In the majority of cases, solute MSDs fall well below the theoretical
  lines and therefore are subject to more hindrance than methanol due to
  factors other than size.

  % 5 and 10 wt %
  \begin{wrapfigure}{r}{0.65\textwidth}
  \centering
  \vspace{-0.4cm}
  \begin{subfigure}{0.45\linewidth}
  \includegraphics[width=\linewidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \includegraphics[width=\linewidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \includegraphics[width=\linewidth]{msd_radius_5wt.pdf}
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \includegraphics[width=\linewidth]{msd_radius_10wt.pdf}
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \vspace{-0.4cm}
  \end{wrapfigure}

  Intermittent hops between long periods of entrapment lead to subdiffusive
  solute transport behavior. As implied by Figures~\ref{fig:msd_radius_10wt} and~\ref{fig:msd_radius_5wt}, 
  most solutes move significantly slower than expected. In 
  Figure~\ref{fig:example_ztraces}, we've plotted the $z$-direction trajectory
  of three ethanol molecules. Typically, long periods of entrapment occur
  when ethanol molecules are far from the pore center, while there is a much 
  greater degree of mobility close to the pore center. The MSD curve averaged
  over all ethanol trajectories is shown in Figure~\ref{fig:example_msd}.
  The curve is sub-linear and thus subdiffusive.

  \begin{wrapfigure}{l}{0.6\textwidth}
  \centering
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and the hops occur when solutes are close to the pore center. (b) The
  time-averaged MSD of ethanol is sub-linear which suggests transport is governed
  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}

  \end{wrapfigure}

  Due to the crowded environment among the monomer tails, solutes generally move
  faster in the less dense pore region. Figure~\ref{fig:hop_lengths} shows that 
  this is the case for all solutes. Hops made in the pore region are on average
  59 \% larger than those made outside the pore region.

  However, time spent in the pore region does not necessarily result
  in a high MSD. For example, ribose spends the largest fraction of time in 
  the pore region, but has the fifth lowest hop frequency and the third 
  lowest average MSD (see Figures~\ref{fig:frac_time} and~\ref{fig:hopfreq}).
  Therefore, proximity to the pore center cannot be the sole variable that
  determines transport properties.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{hop_length.pdf}
  \caption{}\label{fig:hop_lengths}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{frac_time_spent.pdf}
  \caption{}\label{fig:frac_time}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hopfreq_total.pdf}
  \caption{}\label{fig:hopfreq}
  \end{subfigure}
  \caption{(a) Hops made in the pore region of the 10 wt\% water system
  are, on average, 59 \% larger than those made outside the pore region.
  The trend in hop lengths is similar to the trend in MSDs shown in
  Figure~\ref{fig:all_msds_10wt} implying that solutes which make consistently
  larger hops have higher MSDs. The fraction of time spent by a solute in the
  pore region (b) does not necessarily lead to more frequent hopping (c). For
  example, ribose spends the largest fraction of time in the pore region, yet
  performs the the fifth lowest number of hops.}\label{fig:hops}
  \end{figure}

  Among the set of solutes studied, we observe three different mechanisms 
  of entrapment that are responsible for subdiffusive behavior:
  \begin{enumerate}
    \item As already demonstrated by Figures~\ref{fig:example_ztraces} and 
    Figure~\ref{fig:hop_lengths}, solutes that drift away from the pore center
    can become entangled in the monomer tails. 
    \item Many of the solutes we studied are capable of donating hydrogen bonds to
    monomer head groups and thus are prone to temporary immobilization through 
    this interaction.
    \item Because all solutes are polar, they have regions of concentrated electron
    density, modeled as partial charges, which can associate with sodium ions
    bound to monomer head groups.
  \end{enumerate}

  \begin{wrapfigure}{L}{0.7\textwidth}
  \centering
  \vspace{-0.35cm}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{nhbonds_all.pdf}  % unique_hbonds.py
  \caption{}\label{fig:nhbonds}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{hbond_lifetime.pdf}  % hbond_dwells.py
  \caption{}\label{fig:hbond_dwells}
  \end{subfigure}
  \caption{(a) Solutes capable of donating hydrogen bonds to monomer head groups
  do so to varying degrees. The reported percentages represent unique solute-monomer
  hydrogen bonds. Individual solutes that hydrogen bond with multiple head groups
  simultaneously are only counted once. (b) The lifetime of individual hydrogen
  bonds appears correlated to the percentage of solutes involved in hydrogen bond
  interactions. Hydrogen bond lifetimes tend to be longer for solutes that
  hydrogen bond frequently. Note that solutes incapable of donating hydrogen
  bonds are omitted from this figure.}\label{fig:hbonds}
  \vspace{-0.5cm}
  \end{wrapfigure}

  The frequency with which solutes donate hydrogen bonds to monomer head 
  groups is related to the number of hydrogen bond donating atoms as well
  as their identity. The percentage of solutes actively participating in
  at least one hydrogen bond with a head group each frame descends as the
  number of hydroxyl groups decreases (Figure~\ref{fig:nhbonds}). Solutes with many hydroxyl groups,
  such as ribose, tetrose and glycerol, can donate multiple hydrogen bonds
  to monomer head groups simultaneously. When one hydrogen bond is broken,
  other hydrogen bonds work to hold the solute in place, which allows 
  broken hydrogen bonds to reform. Solutes containing sulfur and 
  nitrogen atoms in place of oxygen atoms hydrogen bond less frequently
  since they are less electronegative elements.~\cite{biswal_hydrogen_2015} % citation
  The lifetime of hydrogen bonds follows nearly the same trend 
  (Figure~\ref{fig:hbond_dwells}). Hydrogen bonds of solutes that hydrogen
  bond more frequently last longer.

  \begin{wrapfigure}{r}{0.7\textwidth}
  \centering
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{all_solutes_NA_coordination.pdf}
  \caption{}\label{fig:all_solutes_NA_coordination}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{all_NA_dwells.pdf}
  \caption{}\label{fig:all_NA_dwells}
  \end{subfigure}
  \caption{(a) Solutes, especially those with carbonyl groups, spend a
  significant fraction of time coordinated to sodium ions. (b) The length
  of time a solute-sodium pairs spends associated tends to be higher for
  pairs that associate more frequently.}\label{fig:na_coordination}
  \vspace{-0.5cm}
  \end{wrapfigure}

  Solutes with carbonyl groups tend to associate with sodium ions most frequently.
  Nearly all of the most coordinated solutes contain a carbonyl group, except
  for DMSO which has an analogous sulfinyl group (see Figure~\ref{fig:all_solutes_NA_coordination}). There is a significant drop
  in sodium ion association for solutes that do not contain carbonyl groups or
  multiple hydroxyl groups to compensate.
  The corresponding dwell times follow a similar trend, however the dwell
  times of highly coordinated solutes with multiple hydroxyl groups are generally
  lower since association between hydroxyl groups and sodium is apparently a 
  weaker interaction (Figure~\ref{fig:all_NA_dwells}). Solutes with nitrogen 
  atoms adjacent to the carbonyl groups tend to associate with sodium ions 
  significantly more.

  A manuscript based on the work presented towards this objective is under 
  review for publication in the Journal of Physical Chemistry B.

  \begin{figure}[h!]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{hop_distribution_GCL.pdf}
  \caption{}\label{fig:hop_dist}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{dwell_distribution_GCL.pdf}
  \caption{}\label{fig:dwell_dist}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{hop_acf_GCL.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{The movement of solutes may be well-described by an sFBM process 
  which can be simulated using parameters that describe the solute's hop lengths, 
  dwell times and degree of correlation between hops. Here I use the parameters 
  derived from ethylene glycol as an example. (a) The distribution of hop
  lengths made by ethylene glycol appears Gaussian, which can be described by the
  maximum likelihood estimate (MLE) of the $\sigma$ parameter, with assumed mean, 
  $\mu$, of 0. (b) The distribution of dwell times between hops can be fit to a 
  power law whose decay is described by the MLE of the parameter $\alpha$. 
  (c) Hops are anticorrelated to their previous hop as indicated by the negative
  value at $k=1$ of the autocorrelation function, $\gamma$. The Hurst 
  parameter, $H$, is a measure of long term memory of the hops and is directly
  related to the autocorrelation function of fractional Brownian process.}\label{fig:distributions}
  \end{figure}

  \noindent \textbf{\large Objective 3:} \textit{\large Create a stochastic model} (\textcolor{blue}{\textbf{In Progress}})

  While one can clearly learn a great deal of qualitative information about 
  mechanistic behavior on MD-accessible timescales, my work's impact would
  greatly increase if I could create a model that could predict macroscopic
  quantities such as permeability and selectivity within a reasonable degree
  of certainty. A stochastic model derived from simulation data could achieve 
  this however, there is not a well-defined procedure for this type of 
  extrapolation. Therefore, I am exploring two different approaches towards
  this end.

  \begin{wrapfigure}{r}{0.4\textwidth}
  \centering
  \vspace{-0.6cm}
  \includegraphics[width=\linewidth]{all_tamsds.pdf}
  \caption{The trends in the MSD calculated directly from MD simulations and from
  realizations of the sFBM process mostly agree, but the sFBM predictions are generally
  far too low.}\label{fig:sFBM_MSDs}
  \vspace{-0.5cm}
  \end{wrapfigure}

  \textit{Approach 1: subordinated fraction Brownian motion}: My first route 
  towards a stochastic model is to simulate realizations of a subordinated 
  fractional Brownian motion (sFBM) process based on parameters extracted 
  from solute time series.~\cite{meroz_subdiffusion_2010} As demonstrated 
  by the example in Figures~\ref{fig:hop_dist} and~\ref{fig:dwell_dist},
  hop length distributions in the $z$-direction appear Gaussian while the 
  distribution of dwell times between hops appears to be distributed 
  according to a power law. Alone, these distributions characterize a 
  continuous time random walk (CTRW), which is a subdiffusive process where
  particles hop a random distance in a random direction and stay there for
  a random amount of time.~\cite{meroz_toolbox_2015}. Unlike a CTRW, the 
  hops in our system appear anti-correlated to their previous hop as shown
  by the autocorrelation function in Figure~\ref{fig:hop_acf}. A CTRW with
  anticorrelated hops is well-described by an sFBM process.

  \begin{wrapfigure}{l}{0.6\textwidth}
  \centering
  \vspace{-0.5cm}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{breakpoints.pdf}
  \caption{}\label{fig:breakpoints}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{first_order_difference.pdf}
  \caption{}\label{fig:first_order_difference}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{hop_density.pdf}
  \caption{}\label{fig:hop_density}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{naive_density_forecast.pdf}
  \caption{}\label{fig:naive_density_forecast}
  \end{subfigure}
  \caption{In contrast to our first approach which relies on accurate 
  detection of hops, density forecasting uses all of the time series 
  information at our disposal. (a) Our first approach identifies hops 
  based on breakpoints, indicated by color transitions. All information 
  is lost between breakpoints. (b) Instead we can calculate hop lengths
  between each time step and (c) compile them into a single probability 
  density. (d) As a first approximation, one can simulate time series
  by randomly drawing from the distribution in (c).}\label{fig:density_forecast}
  \vspace{-1.5cm}
  \end{wrapfigure}

  Solute MSDs calculated based on realizations of an sFBM process mostly
  preserve the trends in MSD calculated directly from MD simulations (see
  Figure~\ref{fig:sFBM_MSDs}), but the predictions are generally too low. 
  For each solute, I used the parameters described in Figure~\ref{fig:distributions}
  to generate $1e4$ realizations of an sFBM process, each with the same
  length as the MD simulations (1000 ns) so that I could make a direct 
  comparison between their MSDs. While the sFBM MSD prediction for methanol
  is too high, the rest are on average only 46\% of the MD calculated MSD
  values.

  This approach might be improved by incorporating radial dependence into
  the three sFBM parameters described in Figure~\ref{fig:distributions}. 
  In Figure~\ref{fig:hop_lengths}, we showed that hops by solutes situated 
  inside the pores are 59\% larger than hops by solutes in the tails, which 
  leads to two distinct values of $\sigma$. Similarly, we can determine 
  radially dependent values of $\alpha$ and $H$.

  \begin{wrapfigure}{r}{0.4\textwidth}
  \centering
  \vspace{-0.5cm}
  \includegraphics[width=\linewidth]{z_histogram.pdf}
  \caption{The histogram of $z$ values coming from $z_t$ calculated with 
  Equation~\ref{eqn:pit} appears uniform meaning $p(h)$ is well-sampled 
  by the out-sample data.}\label{fig:z_histogram}
  \vspace{-1cm}
  \end{wrapfigure}

  A simple two state model, in pore versus out of pore, may be sufficient to 
  fully incorporate radially dependent effects. Based on the fraction of time 
  spent in the pore region (Figure~\ref{fig:frac_time}), we can determine
  the appropriate balance of each type of parameter to use when simulating sFBM
  realizations. We would also need some kind of switching frequency, or dwell
  time in each region since it does not make physical sense for a solute to 
  enter and exit the pore region every other time step.

  If the two state model proves insufficient, I can add increasing levels of
  complexity. For example, I might make the radial dependence a continuous 
  function, or I could assign parameters that are dependent on the type of
  trapping mechanism affecting the solute.

  \textit{Approach 2: density forecasting}: Density forecasting can provide
  predictions based on properties of a time series without any knowledge
  of the physical interactions leading to those properties.

  \begin{wrapfigure}{l}{0.6\textwidth}
  \centering
  \vspace{-0.75cm}
  \includegraphics[width=\linewidth]{correlograms.pdf}
  \caption{Correlograms of $z_t$ reveal dependence for all 4 powers of 
  $(z - \overline{z})$.}\label{fig:correlograms}
  \vspace{-0.5cm}
  \end{wrapfigure}

  In contrast to the first approach, density forecasting allows one to use
  all of available trajectory information. In order to construct distributions
  of hop lengths and dwell times with my first approach, I needed to 
  locate precise time points at which hops occurred. We achieved this using 
  an off-line breakpoint detection algorithm implemented in the python package 
  \texttt{ruptures}.~\cite{truong_review_2018} The algorithm does a decent
  job of identifying hops, but still loses information as demonstrated in
  Figure~\ref{fig:breakpoints}. With density forecasting, one can instead 
  compile the hop length and magnitude between each time step 
  (Figure~\ref{fig:first_order_difference}) into a probability density
  like that shown in Figure~\ref{fig:hop_density}. As a first attempt, 
  one could randomly draw from this distribution in order to construct
  a time series like that shown in Figure~\ref{fig:naive_density_forecast}.

  One can test how well a time series of hop lengths, $h_t$, is described by the 
  hop density, $p(h)$, in Figure~\ref{fig:hop_density} using the probability
  integral transform:~\cite{diebold_evaluating_1998}
  \begin{equation}
  z_t = \int_{-\infty}^{h_t} p(u) du
  \label{eqn:pit}
  \end{equation}
  Generally, one uses the first half of a time series, or in-sample data, to
  create $p(h)$ and applies Equation~\ref{eqn:pit} to the second half of
  the time series, or out-sample data. If the distribution of $z_t$ values
  is uniform, then the cumulative distribution function of $p(h)$ has been
  sampled uniformly by the out-sample data and there is evidence that the 
  time series is well-described by $p(h)$. Using the out-sample data from 
  Figure~\ref{fig:density_forecast}, we observe a uniform distribution of
  $z_t$ values (Figure~\ref{fig:z_histogram}).

  However, it is also necessary to look for correlations in $z_t$. Diebold
  et al. found that examination of the correlograms of $(z - \overline{z})$,
  $(z - \overline{z})^2$, $(z - \overline{z})^3$ and $(z - \overline{z})^4$,
  which represent dependence of the mean, variance, skewness and kurtosis 
  respectively, are adequate to identify potentially sophisticated and 
  nonlinear forms of past dependence.~\cite{diebold_evaluating_1998} Continuing
  with our example above, the correlograms of $z_t$ shown in Figure~\ref{fig:correlograms} 
  exhibit serial dependence for all powers of $(z - \overline{z})$. Our 
  time series exhibits dependence on its past values, a feature that was 
  not included in the forecast shown in Figure~\ref{fig:naive_density_forecast}.
  %This likely explains the qualitative difference in the time series of 
  %Figure~\ref{fig:breakpoints} versus~\ref{fig:naive_density_forecast}.

  Going forward, I will need to incorporate previous dependence in the 
  form of a conditional density forecast with the form $p(h|\Omega_t)$ where
  $\Omega_t$ incorporates past hop lengths and radial distances from
  the pore center. These types of autoregressive models have been widely
  studied in the context of economics, but are still well-suited for 
  application to solute transport.~\cite{hamilton_time_1994}

  \noindent \textbf{\large Objective 4:} \textit{\large Apply analyses to 
  Q\textsubscript{I} phase} (\textcolor{blue}{\textbf{In Progress}})

  Paralleling our work on the H\textsubscript{II} phase, my first task towards
  this objective was to build a suitable unit cell representation of the 
  Q\textsubscript{I} phase. Unfortunately, the true space group of the Q\textsubscript{I} phase that we
  are studying is unknown. Experimental diffraction has narrowed down the 
  possible bicontinuous cubic configurations to the Ia3d and Pn3m space groups. 
  Therefore, we will build both types of unit cells and search for clues that
  can be used to differentiate them experimentally.

  \begin{wrapfigure}{l}{0.6\textwidth}
  \centering
  \vspace{-0.5cm}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{gyroid.png}
  \caption{}\label{fig:Ia3d}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{schwarz.png}
  \caption{}\label{fig:pn3m}
  \end{subfigure}
  \caption{I developed a procedure capable of building both (a) Ia3d and (b) Pn3m
  unit cells from arbitrary monomers with controllable pore size. The blue
  glycerol molecules highlight the aqeuous region where transport occurs.}\label{fig:q1_unitcells}
  \vspace{-0.5cm}
  \end{wrapfigure}

  I have developed a procedure that can build both Ia3d and Pn3m unit cells.
  To our knowledge, nobody has ever built an atomistic bicontinuous cubic 
  phase system without the aid of self-assembly. Self-assembly can be a long
  process, especially for fully atomistic systems. Instead, we used known
  analytical equations that describe the surface of these systems in order 
  to place monomers into a unit cell. Monomers are placed perpendicular to
  the surface in random locations that don't overlap. One can control the 
  pore size by translating monomers perpendicular to the surface at the 
  point where they are attached.

  First, I will study the structure of the Q\textsubscript{I} phase using
  methodology similar to that used for the H\textsubscript{II} phase 
  I will attempt to identify one of the space groups as the most likely
  experimental configuration based on simulated XRD signatures, although
  this might not work due to the known similarity of Ia3d and Pn3m XRD 
  patterns. %cite

  Then I will study transport of solutes within these atomistic unit cells, 
  adapting the same analyses used in Objectives 2--3. The primary 
  challenge will be adapting my techniques to the more complex pore geometry
  of the Q\textsubscript{I} phase, however I expect that main conclusions
  will not deviate far from those of the H\textsubscript{II} phase since
  the chemical environments within the nanopores are qualitatively similar.. We may be 
  able to identify which space group is correct if there are significantly
  different transport properties between systems.

%BJC: not sure how much more detail to include. Can go into a lot. Have to expand box and slowly compress. Add glycerol iteratively until there are no gaps.

%  \noindent \textbf{\large Objective 5} \textit{\large Create a well-documented python package} (\textcolor{blue}{\textbf{In Progress}})
%  
%  Python scripts used to simulate X-ray diffraction patterns are available in the following
%  GitHub repository: \url{https://github.com/joeyelk/MD-Structure-Factor}. Documentation
%  is forthcoming. 
%  
%  Python scripts used to conduct all other post-simulation trajectory analysis are 
%  also available on GitHub: \url{https://github.com/shirtsgroup/LLC_Membranes}. 
%  Documentation is a work in progress. It is available for viewing in its 
%  current state at \url{https://llc-membranes.readthedocs.io/en/latest/}.

  \section{Timeline for Completion of Objectives}\label{section:timeline}

  A schematic of the estimated timeline that I plan to follow for the 
  completion of tasks pertinent to finishing all objectives is given 
  in Table~\ref{table:timeline}. Ideally, each task will become a 
  published manuscript. I will run simulations required to 
  study the structure of the bicontinuous cubic phase in
  parallel with the continued development of my stochastic model of 
  transport in the H\textsubscript{II} phase. Simulations and analysis
  required for Q\textsubscript{I} phase solute transport studies analogous
  to those of Objective 2 will be carried out throughout Fall 2019. 
  Application of a stochastic model to the Q\textsubscript{I} phase will
  be finished by May 2020, just before I defend my dissertation.

  \begin{center}  
  \begin{table}[!htb]
	\renewcommand\arraystretch{1.4}\arrayrulecolor{LightSteelBlue3}
	\captionsetup{singlelinecheck=false, font=blue, labelfont=sc, labelsep=quad}
	\caption{Estimated Timeline for Completion of Objectives}\vskip -1.5ex
	\begin{tabular}{@{\,}r <{\hskip 2pt} !{\foo} >{\raggedright\arraybackslash}p{8cm}}
	\toprule
	\addlinespace[1.5ex]
	August 2019 & Complete Stochastic Model for H\textsubscript{II} phase \\
	September 2019 & Finalize Q\textsubscript{I} phase structure \\
    January 2020 & Finish transport study of Q\textsubscript{I} phase \\
    April 2020 & Finish application of stochastic model to Q\textsubscript{I} phase \\
    May 2020 & PhD Defense \\
	\end{tabular}
	\label{table:timeline}
  \end{table}
  \end{center}
  \vspace{-2cm}

  \section{Resource Requirements}\label{section:resources}

  The remainder of our work will require the use of high performance computing (HPC)
  resources. We will continue using Bridges, an XSEDE resource as well as Summit, a
  supercomputer located at CU Boulder.

  \section{Safety Considerations}\label{section:safety}

  Although my work is confined to computer work in an office space, there are 
  associated health risks that I must mitigate. Proper ergonomics ensure 
  maximum comfort and help me to work efficiently. Sitting up straight and
  having proper back support are necessary to relieve pressure on the discs
  of my vertebrae. My monitors are positioned an arm's length directly in 
  front of me with the tops of the monitors at eye level in order to reduce
  head, neck and eye strain. Finally, I take frequent breaks and go for 
  walks around the building.

  \newpage
  \bibliographystyle{ieeetr}
  \bibliography{comps}

\end{document}

### 2019-05-13 Ben_Manuscripts/transport/Draft.tex
Added draft

@@
   particles, with constant molecular volume, did not differ by more than 25\%
-  with most deviating by less than 10\%.~\cite{chan_effects_2015}. 
+  with most deviating by less than 10\%.~\cite{chan_effects_2015-1}. 
   Third, we assume that the ratio of solute and solvent radii as calculated using the
@@
   \section*{Acknowledgments}
+
+  B.J.C. was supported by the Graduate Assistance in Areas of National Need (GAANN) 
+  fellowship which is funded by the U.S. Department of Education.
 

### 2019-05-13 Ben_Manuscripts/comps/figures/legend.py

@@ -1,0 +1,20 @@
+#!/usr/bin/env python
+
+import matplotlib.pyplot as plt
+
+fig, ax = plt.subplots(figsize=(20, 20))
+colors = ['xkcd:blue', 'xkcd:olive', 'xkcd:orangered', 'xkcd:magenta', 'xkcd:gold']
+f = lambda m,c: ax.plot([],[], color=c, linewidth=4)[0]
+handles = [f("s", colors[i]) for i in range(5)]
+print(handles)
+labels = ["Parallel Displaced ($d$ = 3.7 $\AA$)", "Sandwiched ($d$ = 3.7 $\AA$)", "Parallel Displaced ($d$ = 5 $\AA$)", "Sandwiched ($d$ = 5 $\AA$)", "Solvated Parallel Displaced"]
+legend = plt.legend(handles, labels, loc=3, framealpha=1, frameon=False, ncol=3, fontsize=14)
+
+def export_legend(legend, filename="legend.pdf"):
+    fig  = legend.figure
+    fig.canvas.draw()
+    bbox  = legend.get_window_extent().transformed(fig.dpi_scale_trans.inverted())
+    fig.savefig(filename, dpi="figure", bbox_inches=bbox)
+
+export_legend(legend)
+plt.show()

### 2019-05-13 LLC_Membranes/llclib/timeseries.py

@@ -307,6 +307,7 @@ def correlograms(zt):
 
     :type zt: np.ndarray
     """
+
     # Initialize a 2x2 figure
     fig, ax = plt.subplots(2, 2, figsize=(9, 6), sharex=True, sharey=True)
 

### 2019-05-13 Ben_Manuscripts/comps/Draft.tex
comments on the tex

@@
   municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
-  represent a small subset of the diverse contaminants of water sources. 
+  %MRS2: rephrase; sound like you are talking about only a minor problem.  I would suggest adding a few more with citations
+  %MRS2: to show you are aware of the breadth of the subject, and these aren't the only ones you know about.
+  %represent a small subset 
+  are only a few 
+  of the diverse contaminants of water sources. 
   By efficiently separating contaminants from feed solutions with
@@
   permeability of a desired molecular or atomic species, while maintaining
-  the same retention of an undesired species.\cite{werber_materials_2016}
+  the same retention of 
+  %MRS2: an undesired, or all of the undesired?
+an undesired species.\cite{werber_materials_2016}
 
@@
 
+  %MRS2: this section is not so useful, becaue it talks about things you are NOT doing.  In a dissertation, would be good 
+  %MRS2: context, but here, it distracts a bit because it's not summarizing what you are presenting in this paper.
+i.e.
+with 15 pages, you don't want to spend space talking about what you aren't doing.
+Ideally, cut down to 1 paragraph just to
+  %MRS2: show that you are aware of existing technologies.
   Ultrathin-film graphene and graphene oxide membranes are a very active
@@
   (LLC) membranes can be produced at moderate scale and may be capable of 
-  performing highly selective separations. LLCs are amphiphilic molecules 
+  performing highly selective separations. 
+  %MRS2: should be a citation here since you make specific claims.
+  LLCs are amphiphilic molecules 
   that have the ability to self-assemble into porous nanostructures~\cite{smith_ordered_1997}
@@
   periodic uniform-sized pores on the order of 1 nm in diameter~\cite{zhou_supported_2005}. 
-  Since LLC polymer membranes lack an appreciable pore size distribution, they 
+  Since LLC polymer membranes 
+  %MRS2: making a positive statement rather than negative, clearer
+  %lack an appreciable 
+  have a very narrrow
+  pore size distribution, they 
   inherently exhibit high selectivity due to their molecular weight cut-off 
@@
   \noindent There are four primary objectives of this PhD research.
+%MRS2: Explicitly state here that the first two objectives are completed, and that the others are underway.
   \begin{enumerate}
@@
 If phrased in future tense, committee will be confused, thinking those are things still to be done.
+    %MRS2: Objectives shouldn't include a description of what has and hasn't been done.
+Then it's not an really just an objective anymore.
+I would suggest rephrasing these in terms of the intellectual objective, focusing on the questions to be asked and hypotheses to be tested, and then talk in the next section about what has been done (or is to do).
 
@@
     Col\textsubscript{h} phase LLC membrane. I have used this model as an 
-    example in order to understand the ease with which we can apply our approach
+    example in order to 
+    %MRS2: I don't know that it's easy yet . . . 
+    %understand the ease with which 
+    demonstrate how 
+    we can apply our approach
     to alternate monomers and other LC phases.
@@
   of the H\textsubscript{II} phase} (\textcolor{green!40!olive}{\textbf{Complete}})
+  %MRS2: provide paper citation here, rather than at end of section.
 
@@
   time.
-
+  %MRS2: above: less detail on what you did (for example, 400 ns of equilibration); focus on the point of the experiments (whatt hypothesis was tested) and what the results are.
+committee members are going to be less interested in the details than the intellectual framework being used.
   \begin{figure}[!htb]
@@
   \end{subfigure}
+  %MRS2: important consquence of all radian distribution functions being similar is that we should get useful transport details even if we didn't get the structure exactly right. 
   \caption{In all systems studied, the component radial distribution functions are similar.
@@
   \noindent \textbf{\large Objective 2:} \textit{\large Determine transport mechanisms} (\textcolor{green!40!olive}{\textbf{Complete}})
+  %MRS2: put at the beginning it's been submitted.
 
@@
   picture of the pore topology where the pore centers are primarily composed
-  of water and sodium ions. The monomer groups labeled in each plot correspond to
+  of water and sodium ions. 
+  %MRS2: there's actually a lot of head groups in the pores except at the very center.  Does the sentence above
+  %MRS2: communicate that well? 
+The monomer groups labeled in each plot correspond to
   the color-coded monomer pictured in Figure~\ref{fig:HII_mon}. All RDFs
@@
   almost no head groups occupying the pore center.
+  %MRS2: I guess that's not entirely clear to me.
+Yes, at R=0, but most of the pore volume is at R=0.2-0.4, and there are a lot of head groups there.
+There might be a general issue of confusion between ``pore center'' and ``pore regions''
 
@@
   % doesn't count towards the page limit?
+  %MRS2: not sure.  I think there are ways to clear ou space (see above)
+  %MRS2: not great thesis statement.  Thesis statements should be trying to convince reader - this is just listing something you did. 
   We observed transport of 20 different small polar solutes in the pores of
@@
   phase system without the aid of self-assembly. Self-assembly can be a long
-  process, especially for fully atomistic systems. Instead, we used known
+  process, especially for fully atomistic systems. 
+  %MRS2: nobody has built an atomistic model, I think - the self-assembly were for very GC models.
+  Instead, we used known
+  %MRS2: may want to emphasize that for atomistic models, ``long'' is probably at least 2 orders of magnitude longer than our simulations (which are already long)
   analytical equations that describe the surface of these systems in order 
@@
 
+  %MRS2: emphasize comparison to experiments more here, based on what they have done, and what they will do; outline how you will compare to those experiments.
+
 %BJC: not sure how much more detail to include. Can go into a lot. Have to expand box and slowly compress. Add glycerol iteratively until there are no gaps.
+%MRS2: details of how are not that important; focus on what experiments you will do and why.
 

### 2019-05-16 Ben_Manuscripts/comps/Draft.tex
Updates to draft and new figures

--- 2019-05-13 Ben_Manuscripts/comps/Draft.tex
@@
 
-%MRS: overall, really nice start.
-You can cut back a little on the detail and emphasize a bit more ``This is what the data means and what the consequnces are.
-Need to flesh out objective 3 a more (and objective 4 a bit more).
 \author{Benjamin J. Coscia}
@@
 
+    %MRS2: rephrase; sound like you are talking about only a minor problem. I would suggest adding a few more with citations
+  %MRS2: to show you are aware of the breadth of the subject, and these aren't the only ones you know about.
+  %represent a small subset
+  %BJC2: rephrased then added 4 more citations
+
   More highly selective nanoporous membranes would be useful for 
   performing complex aqueous separations with seawater and various
-  types of wastewater. For example, sodium chloride and boron in seawater 
-  \cite{fritzmann_state---art_2007} and organic micropollutants found in
-  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
-  represent a small subset of the diverse contaminants of water sources. 
+  types of wastewater. For example, separating sodium chloride and 
+  boron in seawater could yield potable drinking water in water scarce
+  regions~\cite{fritzmann_state---art_2007} while separation of organic
+  micropollutants found in municipal and industrial wastewaters could 
+  make existing water supplies safer to drink~\cite{schwarzenbach_challenge_2006}.
+  These represent only a few of the diverse contaminants of water sources~\cite{singh_production_2009,liu_removal_2008}. 
   By efficiently separating contaminants from feed solutions with
@@
   requirements and cost. Additionally, one can extract valuable 
-  resources from the feed streams. For example, flowback water produced 
-  during hydraulic fracturing of shale formations contains dissolved 
-  species like acetate whose extraction has economic value \cite{dischinger_application_2017}.
+  resources from the feed streams~\cite{sales_resource_2015}. For example,
+  flowback water produced during hydraulic fracturing of shale 
+  formations contains dissolved species like acetate whose extraction has 
+  economic value \cite{dischinger_application_2017,theodori_hydraulic_2014}.
 
@@
   permeability of a desired molecular or atomic species, while maintaining
-  the same retention of an undesired species.\cite{werber_materials_2016}
+  the same retention of undesired species.\cite{werber_materials_2016}
 
@@
 
+  % BJC2: condensed this section into one paragraph
   Nanostructured membranes attempt to overcome the permeability-selectivity 
-  tradeoff through intelligent design at the molecular level. Graphene sheets, 
-  carbon nanotubes (CNTs) and zeolites are three highly studied nanostructured
-  technologies.
-
-  Ultrathin-film graphene and graphene oxide membranes are a very active
-  area of research because they offer potential for extremely high 
-  permeability membranes. An ideal graphene membrane is a 2D material 
-  composed of a single layer of graphene.\cite{humplik_nanostructured_2011}
-  Synthesis of a single layer of graphene at a large scale without introducing
-  defects is a challenge that has not yet been overcome. Multilayered graphene
-  membranes are potentially easier to synthesize and more scalable which has 
-  resulted in an increasing interest over recent years.\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
-
+  tradeoff through intelligent design at the molecular level. 
+%  Graphene sheets, carbon nanotubes (CNTs) and zeolites are three highly
+%  studied nanostructured technologies. 
+  Ultrathin-film graphene and graphene oxide membranes are an active area
+  of research because they are atomically thick and therefore offer potential
+  for extremely high permeability membranes.~\cite{humplik_nanostructured_2011}
+  However, scalable synthesis without introducing microscopic, performance
+  degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
   Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
   due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001} 
-  Practically, dispersing CNTs into a polymer matrix is extremely difficult
-  because they tend to agglomerate due to Van der Waals forces. Functionalization
-  of the CNT walls has been heavily investigated  as a way to overcome this issue, however 
-  alignment of the CNTs into an array feasible as a nanoporous membrane 
-  persists as a challenge to CNT membranes.\cite{sahoo_polymer_2010}
-
-  Zeolite-coated ceramic membranes offer the potential for permeabilities
+  Practically, dispersing and aligning CNTs into a polymer matrix is extremely
+  difficult because they tend to agglomerate due to Van der Waals forces.~\cite{sahoo_polymer_2010}
+  Finally, zeolite-coated ceramic membranes offer the potential for permeabilities
   comparable to ultrafiltration, molecular sieves with pores up to 100 nm in 
   size~\cite{werber_materials_2016}, with selectivities as good as NF and RO. 
-  Zeolites have highly uniform nm-sized crystalline structures with cage-like
-  cavities that allow movement and trapping of small solutes. The crystalline
-  frameworks are typically formed by networks of silicon and aluminum each 
-  attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
-  One can replace the silicon and aluminum atoms via ion exchange in order to
-  control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}
   A number of studies have tested the permeability and sodium salt rejection
   of various zeolite membranes, however none have fully overcome the 
-  permeability-selectivity tradeoff.~\cite{pendergast_review_2011}
-%    \item Most are prone to defects in the crystalline structure.
+  permeability-selectivity tradeoff.~\cite{pendergast_review_2011,auerbach_handbook_2003,li_novel_2007}
+
+  %MRS2: this section is not so useful, becaue it talks about things you are NOT doing.  In a dissertation, would be good 
+  %MRS2: context, but here, it distracts a bit because it's not summarizing what you are presenting in this paper.
+i.e.
+with 15 pages, you don't want to spend space talking about what you aren't doing.
+Ideally, cut down to 1 paragraph just to
+  %MRS2: show that you are aware of existing technologies.
+  %BJC2: condensed above
+%  Ultrathin-film graphene and graphene oxide membranes are a very active
+%  area of research because they offer potential for extremely high 
+%  permeability membranes. An ideal graphene membrane is a 2D material 
+%  composed of a single layer of graphene.\cite{humplik_nanostructured_2011}
+%  Synthesis of a single layer of graphene at a large scale without introducing
+%  defects is a challenge that has not yet been overcome. Multilayered graphene
+%  membranes are potentially easier to synthesize and more scalable which has 
+%  resulted in an increasing interest over recent years.\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
+%  
+%  Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
+%  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001} 
+%  Practically, dispersing CNTs into a polymer matrix is extremely difficult
+%  because they tend to agglomerate due to Van der Waals forces. Functionalization
+%  of the CNT walls has been heavily investigated  as a way to overcome this issue, however 
+%  alignment of the CNTs into an array feasible as a nanoporous membrane 
+%  persists as a challenge to CNT membranes.\cite{sahoo_polymer_2010}
+%   
+%  
+%  Zeolites have highly uniform nm-sized crystalline structures with cage-like
+%  cavities that allow movement and trapping of small solutes. The crystalline
+%  frameworks are typically formed by networks of silicon and aluminum each 
+%  attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
+%  One can replace the silicon and aluminum atoms via ion exchange in order to
+%  control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}
+%  A number of studies have tested the permeability and sodium salt rejection
+%  of various zeolite membranes, however none have fully overcome the 
+%  permeability-selectivity tradeoff.~\cite{pendergast_review_2011}
+%%    \item Most are prone to defects in the crystalline structure.
 
@@
   (LLC) membranes can be produced at moderate scale and may be capable of 
-  performing highly selective separations. LLCs are amphiphilic molecules 
-  that have the ability to self-assemble into porous nanostructures~\cite{smith_ordered_1997}
-  that can be cross-linked to create mechanically strong membrane films with 
-  periodic uniform-sized pores on the order of 1 nm in diameter~\cite{zhou_supported_2005}. 
-  Since LLC polymer membranes lack an appreciable pore size distribution, they 
+  performing highly selective separations~\cite{zhou_supported_2005,zhou_new_2007}. 
+  LLCs are amphiphilic molecules that have the ability to self-assemble into
+  porous nanostructures~\cite{smith_ordered_1997} that can be cross-linked 
+  to create mechanically strong membrane films with periodic uniform-sized
+  pores on the order of 1 nm in diameter~\cite{zhou_supported_2005}. 
+  Since LLC polymer membranes have a very narrow pore size distribution, they 
   inherently exhibit high selectivity due to their molecular weight cut-off 
@@
 
-  % BJC: should show figure with HII and QI monomer structures
   The feasibility of nanostructured LLC polymer membranes for selective separations
@@
 
-  \noindent There are four primary objectives of this PhD research.
+  \noindent There are four primary objectives of this PhD research which are 
+  at various stages of completion.
+
   \begin{enumerate}
@@
     \item Develop techniques to build and understand the nanoscopic structure
-    of LLC membranes.
-
-    %MRS: probably should talk about this 1) with proper tense (some of these things have been done) and 2) talk about what YOU are doing, not we.
-I helped design the research, but you carried essentially all of it out!
-If phrased in future tense, committee will be confused, thinking those are things still to be done.
+    of LLC membranes. (\textcolor{green!40!olive}{\textbf{Complete}})
+
+    %MRS2: Objectives shouldn't include a description of what has and hasn't 
+    %been done.  Then it's not an really just an objective anymore. I would 
+    %suggest rephrasing these in terms of the intellectual objective, focusing
+    %on the questions to be asked and hypotheses to be tested, and then talk 
+    %in the next section about what has been done (or is to do).
+    %BJC2: got it, rephrased first 2 objectives.
 
@@
     the role of monomer structure in solute transport and membrane design.
-    I have created a maximally consistent structural model by comparing 
-    simulated X-ray diffraction (XRD) patterns, generated from MD trajectories,
-    to an experimental 2D wide angle X-ray scattering (WAXS) spectrum of a 
-    Col\textsubscript{h} phase LLC membrane. I have used this model as an 
-    example in order to understand the ease with which we can apply our approach
-    to alternate monomers and other LC phases.
+    Therefore, we must first create an atomistic model that is maximally 
+    consistent with experimental structural data. It is also necessary to
+    evaluate and justify the minimum effort required to build systems with
+    alternate monomers while maintaining an experimentally-consistent 
+    chemical environment.
+
+%    I have created a maximally consistent structural model by comparing 
+%    simulated X-ray diffraction (XRD) patterns, generated from MD trajectories,
+%    to an experimental 2D wide angle X-ray scattering (WAXS) spectrum of a 
+%    Col\textsubscript{h} phase LLC membrane. I have used this model as an 
+%    example in order to 
+%    %MRS2: I don't know that it's easy yet . . . 
+%    %understand the ease with which 
+%    demonstrate how 
+%    we can apply our approach
+%    to alternate monomers and other LC phases.
 
@@
 
-    \item Determine dominant solute-membrane interactions that give rise to
-    transport mechanisms.
-
-    I observed the transport of a relatively large set of small polar solutes
-    placed within the H\textsubscript{II} phase membrane nanopores. I analyzed
-    the time series of each solute's position in addition to directly measuring
-    the physical interactions, such as hydrogen bonding and ion coordination, 
-    between solutes and LLC monomers.
+    \item Determine solute-membrane interactions that give rise to
+    transport mechanisms. (\textcolor{green!40!olive}{\textbf{Complete}})
+
+    Using my most experimentally consistent configuration, I can place 
+    small molecules within the H\textsubscript{II} nanopores and observe
+    their behavior over simulation-accessible timescales. This objective 
+    aims to organize observations of various solute behaviors into
+    distinct mechanisms that can help guide membrane design based on 
+    chemical functionality of both solutes and LLC monomers.
+
+%    I observed the transport of a relatively large set of small polar solutes
+%    placed within the H\textsubscript{II} phase membrane nanopores. I analyzed
+%    the time series of each solute's position in addition to directly measuring
+%    the physical interactions, such as hydrogen bonding and ion coordination, 
+%    between solutes and LLC monomers.
 
     \item Create a stochastic model which can project long timescale 
-    transport behavior.
+    transport behavior. (\textcolor{blue}{\textbf{In Progress}})
 
@@
 
-    \item Adapt the same analysis to the Q\textsubscript{I} phase.
+    \item Adapt the same analysis to the Q\textsubscript{I} phase. (\textcolor{blue}{\textbf{In Progress}})
 
@@
 
-%MRS: overall, good description of wha has been done.  You can cut back a little if space is an issue.  Give the paper citations with the points. 
   \section{Progress to Date}\label{section:progress}
@@
   of the H\textsubscript{II} phase} (\textcolor{green!40!olive}{\textbf{Complete}})
+
+  %BJC2: maybe a better way to present this
+  \noindent My work fulfilling this objective is published in the Journal of Physical 
+  Chemistry B: Coscia et al. \textit{J. Phys. Chem. B}, 123, 289-309 (2019).
 
@@
   compared the structure to experimental data for a system claimed to be
-  synthesized with only neat monomer. I equilibrated unit cells using a series
-  of simulations with head groups held in place by position restraints, gradually
-  reducing the force constant of the position restraints until the system
-  was completely unrestrained. I let the system equilibrate for 400 ns of simulation
-  time.
+  synthesized with only neat monomer.
+
+  %BJC2: removing unnecessary details
+%  I equilibrated unit cells using a series
+%  of simulations with head groups held in place by position restraints, gradually
+%  reducing the force constant of the position restraints until the system
+%  was completely unrestrained. I let the system equilibrate for 400 ns of simulation
+%  time.
+
+  %MRS2: above: less detail on what you did (for example, 400 ns of equilibration); 
+  %focus on the point of the experiments (whatt hypothesis was tested) and what the 
+  %results are.  committee members are going to be less interested in the details 
+  %than the intellectual framework being used.
+  %BJC2: implementing this idea throughout
 
@@
   monomers in parallel displaced and sandwiched configurations, two possible
-  $\pi$-$\pi$ stacking modes.\cite{sinnokrot_estimates_2002} I also varied 
-  the initial distance between stacked monomers, $d$. I chose $d$ values of 
-  3.7~\AA, based on experimental WAXS measurements, as well as 5 \AA~as a 
-  test of its sensitivity.
+  $\pi$-$\pi$ stacking modes that might occur between monomer phenyl groups.
+  ~\cite{sinnokrot_estimates_2002} I also varied the initial distance between
+  stacked monomers, $d$. I chose $d$ values of 3.7~\AA, based on experimental
+  WAXS measurements, as well as 5 \AA~as a test of its sensitivity.
 
@@
             each pore increases.}~\label{fig:p2p}
-    \vspace{-1.75cm}
+    \vspace{-1.25cm}
   \end{wrapfigure}
@@
   reflections and the structural features leading to them are summarized
-  and described in the caption of Figure~\ref{fig:WAXS_comparison}. None of
-  the models simulated to this point could reproduce R-double.
+  and described in the caption of Figure~\ref{fig:WAXS_comparison}. Note that
+  none of the models simulated to this point could reproduce R-double.
 
@@
   in the parallel displaced configuration with 1 wt\% water added to the pores. 
-  This is the only configuration that gives rise to the R-double feature. R-double
-  appears because vertically adjacent monomer head groups hydrogen bond with shared 
-  water molecules, causing them to be drawn closer together. When multiple 
-  pairing interactions occur in series along the same pore axis, the center
-  of masses of the pairs are spaced apart at twice the $\pi$-stacking distance. 
-  The necessity of water in my model suggests that the membrane synthesized by
-  Feng et al. was slightly hydrated due to water molecules leached from 
-  surroundings by the hydroscopic monomers. Similar suspicions have been voiced
-  by experimentalists in unpublished communications.
+  This is the only configuration that gives rise to the R-double feature without
+  imposing some kind of position restraint. R-double appears because 
+  vertically adjacent monomer head groups hydrogen bond with shared water molecules,
+  causing them to be drawn closer together. When multiple pairing interactions
+  occur in series along the same pore axis, the center of masses of the pairs 
+  are spaced apart at twice the $\pi$-stacking distance. The necessity of water
+  in my model suggests that the membrane synthesized by Feng et al.
+  ~\cite{feng_scalable_2014,feng_thin_2016} was slightly hydrated due to water 
+  molecules leached from surroundings by the hydroscopic monomers. Similar 
+  suspicions have been voiced by experimentalists in unpublished communications.
 
@@
     (R-double) Monomer head groups associate into pairs by hydrogen bonding with
-    a shared water molecule. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. 
-    (R-spots) Monomer tails pack hexagonally. (R-pores) The pores are spaced 
-    4.12 nm apart and pack hexagonally. (b) We obtain a maximally consistent
-    match between simulated XRD patterns and experimental WAXS data when we
-    build systems in the parallel displaced configuration with 1 wt \% water
-    included in the pores.}\label{fig:WAXS_comparison}
+    a shared water molecule. R-double does not appear in dry systems. 
+    (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer tails
+    pack hexagonally. (R-pores) The pores are spaced 4.12 nm apart and pack 
+    hexagonally. (b) We obtain a maximally consistent match between simulated
+    XRD patterns and experimental WAXS data when we build systems in the 
+    parallel displaced configuration with 1 wt \% water included in the pores.
+    }\label{fig:WAXS_comparison}
     \vspace{-0.75cm}
@@
 
-  %BJC: I think this is important to say somewhere
-  %BJC: but I don't have an ensemble of 1 wt % systems to fully prove that with.
-  %BJC: I could show cross-sections of R-pi, but that would require more context. 
-  On the timescales that we can reasonably simulate, our model exhibits slow 
-  dynamics. Consequently, there are very few uncorrelated frames in our 
+  On the timescales that one can reasonably simulate, my model exhibits slow 
+  dynamics. Consequently, there are very few uncorrelated frames in the 
   trajectories which leads to noise and sharpened reflections in the simulated
-  XRD patterns. We can overcome this issue by combining the structure factors
-  generated from an ensemble of trajectories produced starting from an ensemble
-  of uncorrelated initial configurations.
-
-  The composition of the pores does not change regardless of which
-  initial configuration we study. In Figure~\ref{fig:overlaid_densities}, we 
-  plot the radial density of various monomer components as a function of distance
-  from the pore centers. All are qualitatively similar meaning that a solute 
-  placed in any of these systems should experience a similar chemical environment.
-  Although we will move forward with our most promising configuration, this is 
-  an important finding since it implies that we do not need to apply the same level
-  of rigor when screening new monomers.
-
-  My work towards this objective is published in the Journal of Physical Chemistry B:
-  Coscia et al. \textit{J. Phys. Chem. B}, 123, 289-309 (2019).
+  XRD patterns. One can overcome this issue by combining the structure factors
+  generated from an ensemble of simulated trajectories each produced
+  from an ensemble of uncorrelated initial configurations. One can create 
+  decorrelated initial configurations by randomly displacing monomer columns in
+  the $z$-direction.
+
+  Perhaps the most important conclusion from my structural work is that the 
+  chemical composition of the pores is relatively insensitive to the initial 
+  configuration. In Figure~\ref{fig:overlaid_densities}, I plot the radial 
+  distribution function of various monomer components as a function of distance
+  from the closest pore center. All are qualitatively similar meaning that a 
+  solute placed in any of these systems should experience a similar chemical 
+  environment. Although we will move forward with our most promising 
+  configuration, this is an important finding since it implies that one does
+  not need to apply the same level of rigor when screening new monomers.
 
@@
 
-  We added additional water to our most experimentally consistent structural
+  \noindent A manuscript based on the work presented towards this objective is under 
+  review for publication in the Journal of Physical Chemistry B.
+
+  I added additional water to the most experimentally consistent structural
   model in order to create a higher water content H\textsubscript{II} phase
@@
   the NaGA3C11 monomer with water contents ranging from 7 - 20 wt\%, with 
-  10 wt\% being the most common.~\cite{smith_ordered_1997,zhou_supported_2005} 
+  close to 10 wt\% being the most common.~\cite{smith_ordered_1997,zhou_supported_2005} 
   However, Resel et al. stated that the system is likely fully hydrated at
-  7 wt \% water with additional water trapped in defects between mesophases.~\cite{resel_structural_2000}
-  Consequently, we chose to build two systems with 5 and 10 wt\% water.
+  7 wt \% water with additional water trapped in defects between hexagonal
+  mesophases.~\cite{resel_structural_2000} Consequently, we chose to build
+  two systems with 5 and 10 wt\% water.
+
+  Upon simulating each system, we observed that water partitions into the
+  distal tail region. Based on the radial distance from the pore center where 
+  the minimum water density occurs, we defined the distal tail region to 
+  be greater than 1.5 nm from any pore center. There is approximately a 3:2
+  ratio of water in the pores to water in the distal tails. Due to the wedge
+  shape of the monomers, the distal tail region has a relatively low density
+  leaving space for water molecules to fill.
 
@@
   \centering
-  \vspace{-0.4cm}
+%  \vspace{-0.3cm}
 %  \begin{subfigure}{0.325\textwidth}
@@
   \caption{The radial densities of various monomer components paint a
-  picture of the pore topology where the pore centers are primarily composed
-  of water and sodium ions. The monomer groups labeled in each plot correspond to
+  picture of the pore topology where the pore centers are primarily 
+  composed of water, sodium ions and head groups to varying degrees
+  depending on total water composition.
+  %MRS2: there's actually a lot of head groups in the pores except at the very center.  Does the sentence above
+  %MRS2: communicate that well? 
+  %BJC2: rephrased.
+  The monomer groups labeled in each plot correspond to
   the color-coded monomer pictured in Figure~\ref{fig:HII_mon}. All RDFs
@@
   peaks closer to the head groups since many stay bound to carboxylate groups.}\label{fig:component_densities}
-  \vspace{-0.75cm}
+  \vspace{-0.5cm}
   \end{wrapfigure}
 
-  Upon simulating each system, we observed that water partitions into the
-  distal tail region. Based on the radial distance from the pore center where 
-  the minimum water density occurs, we defined the distal tail region to 
-  be greater than 1.5 nm from any pore center. There
-  is approximately a 3:2 ratio of water in the pores to water in the 
-  distal tails. Due to the wedge shape of the monomers, the distal tail
-  region has a relatively low density leaving space for water molecules 
-  to fill.
-
-  The pores of the H\textsubscript{II} phase are primarily a mixture of 
-  water and sodium ions. The maximum density of head groups occurs 0.45
-  and 0.65 nm from the pore center in the 5 and 10 wt\% water systems 
-  respectively (see Figure~\ref{fig:component_densities}). There are 
-  almost no head groups occupying the pore center.
+  The pores of the H\textsubscript{II} phase are a mixture of water, sodium
+  ions and monomer head groups. Water is densest at the pore center ($r = 0$).
+  The maximum density of head groups occurs 0.45 and 0.65 nm from the pore 
+  center in the 5 and 10 wt\% water systems respectively (see 
+  Figure~\ref{fig:component_densities}).
+
+  %There are almost no head groups 
+  %occupying the pore center.
+  %MRS2: I guess that's not entirely clear to me.
+Yes, at R=0, but most of the pore volume is at R=0.2-0.4, and there are a lot of head groups there.
+There might be a general issue of confusion between ``pore center'' and ``pore regions''
+  %BJC2: Avoiding the confusion. I think saying this makes more sense when comparing
+  %directly to the dry system which has a significant head group density at R=0.
 
@@
 
-  % BJC: do you think I can get away with an appendix with the solute table + abbreviations that
-  % doesn't count towards the page limit?
-  We observed transport of 20 different small polar solutes in the pores of
-  our model. We created a separate initial configuration for each solute 
-  studied and placed 6 solutes, equally spaced in $z$, in each nanopore.
-  After a 5 ns equilibration, we allowed the solutes to simulate for
-  1 microsecond.
+  %MRS2: not great thesis statement.  Thesis statements should be trying to convince reader - this is just listing something you did. 
+  %BJC2: tried again.
+  I explored the influence of a solute's chemical functionality on its 
+  transport properties within the H\textsubscript{II} nanopores using simulations
+  of 20 different small polar solutes (see Table~\ref{fig:solute_table}).
+  For each solute, I created a separate initial configuration and placed 6 
+  solutes, equally spaced in $z$, in each nanopore. This gave a sufficient
+  number of solute trajectories from which to generate statistics while 
+  maintaining a low degree of interaction between solutes.
+
+  % Unnecessary details
+  % After a 5 ns equilibration, we allowed the solutes to simulate for
+  % 1 microsecond.
 
@@
 %  \end{wrapfigure}
+    % 5 and 10 wt %
 
@@
   the average MSD of each solute. In Figure~\ref{fig:msd_radius_5wt} 
-  and~\ref{fig:msd_radius_10wt}, we plot solute MSDs against their
-  molecular radius. We also show theoretical curves which illustrate the 
-  expected MSD of each solute if they were to travel unhindered. We 
-  ensured that the Stokes-Einstein equation with the correction factor
-  of Gierer and Wirtz\cite{gierer_molekulare_1953} passed through methanol's MSD and radius
-  in order to give an approximate frame of reference. The correction 
+  and~\ref{fig:msd_radius_10wt}, I plotted the solute MSDs against their
+  molecular radius. Also plotted are theoretical curves which illustrate the 
+  expected MSD of each solute if they were to travel unhindered. The 
+  Stokes-Einstein equation with the correction factor of Gierer and 
+  Wirtz~\cite{gierer_molekulare_1953} passes through methanol's MSD and
+  radius in order to give an approximate frame of reference. The correction 
   factor attempts to include the effects of microfriction that begin to 
   play a role when solute size becomes on the order of solvent size. 
-  Since methanol is small, we assume that it travels unhindered relative 
+  Since methanol is small, I assume that it travels unhindered relative 
   to all other solutes. The theoretical line serves as an approximate 
@@
 
-  % 5 and 10 wt %
   \begin{wrapfigure}{r}{0.65\textwidth}
@@
   most solutes move significantly slower than expected. In 
-  Figure~\ref{fig:example_ztraces}, we've plotted the $z$-direction trajectory
+  Figure~\ref{fig:example_ztraces}, I've plotted the $z$-direction trajectory
   of three ethanol molecules. Typically, long periods of entrapment occur
@@
   example, ribose spends the largest fraction of time in the pore region, yet
-  performs the the fifth lowest number of hops.}\label{fig:hops}
+  performs the the fifth lowest number of hops and third lowest MSD.}\label{fig:hops}
   \end{figure}
@@
   at least one hydrogen bond with a head group each frame descends as the
-  number of hydroxyl groups decreases (Figure~\ref{fig:nhbonds}). Solutes with many hydroxyl groups,
-  such as ribose, tetrose and glycerol, can donate multiple hydrogen bonds
-  to monomer head groups simultaneously. When one hydrogen bond is broken,
-  other hydrogen bonds work to hold the solute in place, which allows 
-  broken hydrogen bonds to reform. Solutes containing sulfur and 
-  nitrogen atoms in place of oxygen atoms hydrogen bond less frequently
-  since they are less electronegative elements.~\cite{biswal_hydrogen_2015} % citation
+  number of hydroxyl groups decreases (Figure~\ref{fig:nhbonds}). Solutes
+  with many hydroxyl groups, such as ribose, tetrose and glycerol, can 
+  donate multiple hydrogen bonds to monomer head groups simultaneously. 
+  When one hydrogen bond is broken, other hydrogen bonds work to hold the
+  solute in place, which allows broken hydrogen bonds to reform. Solutes 
+  containing sulfur and nitrogen atoms in place of oxygen atoms hydrogen
+  bond less frequently since they are less electronegative elements.~\cite{biswal_hydrogen_2015} % citation
   The lifetime of hydrogen bonds follows nearly the same trend 
@@
   Nearly all of the most coordinated solutes contain a carbonyl group, except
-  for DMSO which has an analogous sulfinyl group (see Figure~\ref{fig:all_solutes_NA_coordination}). There is a significant drop
+  for DMSO which has an analogous sulfinyl group (see 
+  Figure~\ref{fig:all_solutes_NA_coordination}). There is a significant drop
   in sodium ion association for solutes that do not contain carbonyl groups or
-  multiple hydroxyl groups to compensate.
-  The corresponding dwell times follow a similar trend, however the dwell
-  times of highly coordinated solutes with multiple hydroxyl groups are generally
-  lower since association between hydroxyl groups and sodium is apparently a 
-  weaker interaction (Figure~\ref{fig:all_NA_dwells}). Solutes with nitrogen 
-  atoms adjacent to the carbonyl groups tend to associate with sodium ions 
-  significantly more.
-
-  A manuscript based on the work presented towards this objective is under 
-  review for publication in the Journal of Physical Chemistry B.
+  multiple hydroxyl groups to compensate. The corresponding dwell times 
+  follow a similar trend, however the dwell times of highly coordinated solutes
+  with multiple hydroxyl groups are generally lower since association between
+  hydroxyl groups and sodium is apparently a weaker interaction 
+  (Figure~\ref{fig:all_NA_dwells}). Solutes with nitrogen atoms adjacent to 
+  the carbonyl groups tend to associate with sodium ions significantly more.
 
@@
   parameter, $H$, is a measure of long term memory of the hops and is directly
-  related to the autocorrelation function of fractional Brownian process.}\label{fig:distributions}
+  related to the autocorrelation function of a fractional Brownian process.}\label{fig:distributions}
   \end{figure}
@@
   fractional Brownian motion (sFBM) process based on parameters extracted 
-  from solute time series.~\cite{meroz_subdiffusion_2010} As demonstrated 
-  by the example in Figures~\ref{fig:hop_dist} and~\ref{fig:dwell_dist},
-  hop length distributions in the $z$-direction appear Gaussian while the 
-  distribution of dwell times between hops appears to be distributed 
-  according to a power law. Alone, these distributions characterize a 
-  continuous time random walk (CTRW), which is a subdiffusive process where
-  particles hop a random distance in a random direction and stay there for
-  a random amount of time.~\cite{meroz_toolbox_2015}. Unlike a CTRW, the 
-  hops in our system appear anti-correlated to their previous hop as shown
-  by the autocorrelation function in Figure~\ref{fig:hop_acf}. A CTRW with
-  anticorrelated hops is well-described by an sFBM process.
-
-  \begin{wrapfigure}{l}{0.6\textwidth}
-  \centering
-  \vspace{-0.5cm}
-  \begin{subfigure}{0.49\linewidth}
-  \includegraphics[width=\linewidth]{breakpoints.pdf}
-  \caption{}\label{fig:breakpoints}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-  \includegraphics[width=\linewidth]{first_order_difference.pdf}
-  \caption{}\label{fig:first_order_difference}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-  \includegraphics[width=\linewidth]{hop_density.pdf}
-  \caption{}\label{fig:hop_density}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-  \includegraphics[width=\linewidth]{naive_density_forecast.pdf}
-  \caption{}\label{fig:naive_density_forecast}
-  \end{subfigure}
-  \caption{In contrast to our first approach which relies on accurate 
-  detection of hops, density forecasting uses all of the time series 
-  information at our disposal. (a) Our first approach identifies hops 
-  based on breakpoints, indicated by color transitions. All information 
-  is lost between breakpoints. (b) Instead we can calculate hop lengths
-  between each time step and (c) compile them into a single probability 
-  density. (d) As a first approximation, one can simulate time series
-  by randomly drawing from the distribution in (c).}\label{fig:density_forecast}
-  \vspace{-1.5cm}
-  \end{wrapfigure}
+  from solute time series. As demonstrated by the example in 
+  Figures~\ref{fig:hop_dist} and~\ref{fig:dwell_dist}, hop length 
+  distributions in the $z$-direction appear Gaussian while the distribution
+  of dwell times between hops appears to be distributed according to a power
+  law. Alone, these distributions characterize a continuous time random walk
+  (CTRW), which is a subdiffusive process where particles hop a random distance
+  in a random direction and stay there for a random period of time.~\cite{meroz_toolbox_2015}.
+  Unlike a CTRW, the hops in the system I study appear anti-correlated to 
+  their previous hop as demonstrated by the autocorrelation function in 
+  Figure~\ref{fig:hop_acf}. A CTRW with anticorrelated hops is well-described
+  by an sFBM process.~\cite{meroz_subdiffusion_2010}
+
+%  \begin{wrapfigure}{l}{0.6\textwidth}
+%  \centering
+%  \vspace{-0.5cm}
+%  \begin{subfigure}{0.49\linewidth}
+%  \includegraphics[width=\linewidth]{breakpoints.pdf}
+%  \caption{}\label{fig:breakpoints}
+%  \end{subfigure}
+%  \begin{subfigure}{0.49\linewidth}
+%  \includegraphics[width=\linewidth]{first_order_difference.pdf}
+%  \caption{}\label{fig:first_order_difference}
+%  \end{subfigure}
+%  \begin{subfigure}{0.49\linewidth}
+%  \includegraphics[width=\linewidth]{hop_density.pdf}
+%  \caption{}\label{fig:hop_density}
+%  \end{subfigure}
+%  \begin{subfigure}{0.49\linewidth}
+%  \includegraphics[width=\linewidth]{naive_density_forecast.pdf}
+%  \caption{}\label{fig:naive_density_forecast}
+%  \end{subfigure}
+%  \caption{In contrast to our first approach which relies on accurate 
+%  detection of hops, density forecasting uses all of the time series 
+%  information at our disposal. (a) Our first approach identifies hops 
+%  based on breakpoints, indicated by color transitions. All information 
+%  is lost between breakpoints. (b) Instead we can calculate hop lengths
+%  between each time step and (c) compile them into a single probability 
+%  density. (d) As a first approximation, one can simulate time series
+%  by randomly drawing from the distribution in (c).}\label{fig:density_forecast}
+%  \vspace{-1.5cm}
+%  \end{wrapfigure}
 
@@
 
+%  \begin{wrapfigure}{r}{0.4\textwidth}
+%  \centering
+%  \vspace{-0.5cm}
+%  \includegraphics[width=\linewidth]{z_histogram.pdf}
+%  \caption{The histogram of $z$ values coming from $z_t$ calculated with 
+%  Equation~\ref{eqn:pit} appears uniform meaning $p(h)$ is well-sampled 
+%  by the out-sample data.}\label{fig:z_histogram}
+%  \vspace{-1cm}
+%  \end{wrapfigure}
+
+  \begin{wrapfigure}{l}{0.4\textwidth}
+  \centering
+  \vspace{-0.5cm}
+  \begin{subfigure}{\linewidth}
+  \includegraphics[width=\linewidth]{breakpoints.pdf}
+  \caption{}\label{fig:breakpoints}
+  \end{subfigure}
+  \caption{In order to generate the parameters used in our first approach,
+  I identified hops based on change points in the time series, indicated by
+  color transitions. In addition to errors in change point detection, all 
+  information between change points is lost.}\label{fig:ruptures}
+  \vspace{-.5cm}
+  \end{wrapfigure}
+
   This approach might be improved by incorporating radial dependence into
@@
   radially dependent values of $\alpha$ and $H$.
-
-  \begin{wrapfigure}{r}{0.4\textwidth}
-  \centering
-  \vspace{-0.5cm}
-  \includegraphics[width=\linewidth]{z_histogram.pdf}
-  \caption{The histogram of $z$ values coming from $z_t$ calculated with 
-  Equation~\ref{eqn:pit} appears uniform meaning $p(h)$ is well-sampled 
-  by the out-sample data.}\label{fig:z_histogram}
-  \vspace{-1cm}
-  \end{wrapfigure}
 
@@
 
-  \textit{Approach 2: density forecasting}: Density forecasting can provide
-  predictions based on properties of a time series without any knowledge
-  of the physical interactions leading to those properties.
-
-  \begin{wrapfigure}{l}{0.6\textwidth}
-  \centering
-  \vspace{-0.75cm}
-  \includegraphics[width=\linewidth]{correlograms.pdf}
-  \caption{Correlograms of $z_t$ reveal dependence for all 4 powers of 
-  $(z - \overline{z})$.}\label{fig:correlograms}
+  It is important to note that this first approach throws out a significant fraction
+  of the data. In order to construct distributions of hop lengths and dwell 
+  times with my first approach, I needed to locate precise time points at which
+  hops occurred. We achieved this using an off-line change point detection algorithm implemented
+  in the python package \texttt{ruptures}.~\cite{truong_review_2018} The 
+  algorithm does a decent job of identifying hops, but still loses information
+  as demonstrated in Figure~\ref{fig:breakpoints}.
+
+  \textit{Approach 2: Markov Switching Models}: Instead of limiting my 
+  analysis to 3 fitting parameters ($\alpha$, $\sigma$ and $H$), my second
+  approach uses all of the available data in order to classify sequences
+  of time series behavior into distinct states. In 
+  Figure~\ref{fig:markov_states_timeseries}, for demonstrative purposes,
+  I've identified 3 potential states defined by the solute's behavior 
+  during the time bounded by each box. Once we've identified states, we 
+  can use our data to define a matrix of probabilities describing switches
+  between states, following a Markovian framework (see Figure~\ref{fig:markov}).~\cite{howard_dynamic_1960}
+
+  \begin{figure}
+  \centering
   \vspace{-0.5cm}
-  \end{wrapfigure}
-
-  In contrast to the first approach, density forecasting allows one to use
-  all of available trajectory information. In order to construct distributions
-  of hop lengths and dwell times with my first approach, I needed to 
-  locate precise time points at which hops occurred. We achieved this using 
-  an off-line breakpoint detection algorithm implemented in the python package 
-  \texttt{ruptures}.~\cite{truong_review_2018} The algorithm does a decent
-  job of identifying hops, but still loses information as demonstrated in
-  Figure~\ref{fig:breakpoints}. With density forecasting, one can instead 
-  compile the hop length and magnitude between each time step 
-  (Figure~\ref{fig:first_order_difference}) into a probability density
-  like that shown in Figure~\ref{fig:hop_density}. As a first attempt, 
-  one could randomly draw from this distribution in order to construct
-  a time series like that shown in Figure~\ref{fig:naive_density_forecast}.
-
-  One can test how well a time series of hop lengths, $h_t$, is described by the 
-  hop density, $p(h)$, in Figure~\ref{fig:hop_density} using the probability
-  integral transform:~\cite{diebold_evaluating_1998}
+  \begin{subfigure}{0.725\linewidth}
+  \includegraphics[width=\linewidth]{markov_states_timeseries.png}
+  \caption{}\label{fig:markov_states_timeseries}
+  \end{subfigure}
+  \begin{subfigure}{0.25\linewidth}
+  \includegraphics[width=\linewidth]{markov.png}
+  \caption{}\label{fig:markov}
+  \end{subfigure}
+  \caption{Using my second approach, I will be able to classify the behavior
+  of solutes into distinct states. (a) As an example, I've come up with three
+  potential states based on the time series pictured above. State 1: solutes
+  far from the pore region are trapped in the tails leading to restricted 
+  motion. State 2: unbound solutes within the pores make large and frequent
+  movements. State 3: solutes donating hydrogen bonds to monomer head groups
+  tend to stay in place. (b) There is a probability associated with each
+  transition between states, represented by the arrows above. For example, following
+  the red arrows, there are probabilities associated with going from State 1 to
+  State 2, from State 1 to State 3 and from State 1 back to State 1.
+  }\label{fig:markov_states}
+  \vspace{-.5cm}
+  \end{figure}
+
+  I will use the Kalman filter algorithm in order to identify distinct states
+  in solute time series and simultaneously describe the dynamics of each state.~\cite{kalman_new_1960}
+  In general, the Kalman filter can attempt to linearly project subsequent 
+  steps in a time series based on its past values. The error in each prediction
+  is stored sequentially. Regions of the time series associated with the 
+  largest prediction uncertainties can be used as an indication of a state change.
+  Using a non-parametric Bayesian approach to identify states, I will not need to 
+  pre-define the number of states which will allow the data to drive the
+  model's complexity.~\cite{lee_unraveling_2017} A convenient byproduct of the Kalman
+  filter are maximum likelihood estimates for parameters which describe the times
+  series in terms of an autoregressive moving average (ARMA) process:~\cite{hamilton_time_1994}
   \begin{equation}
-  z_t = \int_{-\infty}^{h_t} p(u) du
-  \label{eqn:pit}
+  Y_t = c + \phi_1 Y_{t-1} + \phi_2 Y_{t-2} + \cdot\cdot\cdot + \phi_p Y_{t-p} + \epsilon_t + \theta_1\epsilon_{t-1} + \theta_2\epsilon_{t-2} + \cdot\cdot\cdot + \theta_q\epsilon_{t-q}
+  \label{eqn:arma}
   \end{equation}
-  Generally, one uses the first half of a time series, or in-sample data, to
-  create $p(h)$ and applies Equation~\ref{eqn:pit} to the second half of
-  the time series, or out-sample data. If the distribution of $z_t$ values
-  is uniform, then the cumulative distribution function of $p(h)$ has been
-  sampled uniformly by the out-sample data and there is evidence that the 
-  time series is well-described by $p(h)$. Using the out-sample data from 
-  Figure~\ref{fig:density_forecast}, we observe a uniform distribution of
-  $z_t$ values (Figure~\ref{fig:z_histogram}).
-
-  However, it is also necessary to look for correlations in $z_t$. Diebold
-  et al. found that examination of the correlograms of $(z - \overline{z})$,
-  $(z - \overline{z})^2$, $(z - \overline{z})^3$ and $(z - \overline{z})^4$,
-  which represent dependence of the mean, variance, skewness and kurtosis 
-  respectively, are adequate to identify potentially sophisticated and 
-  nonlinear forms of past dependence.~\cite{diebold_evaluating_1998} Continuing
-  with our example above, the correlograms of $z_t$ shown in Figure~\ref{fig:correlograms} 
-  exhibit serial dependence for all powers of $(z - \overline{z})$. Our 
-  time series exhibits dependence on its past values, a feature that was 
-  not included in the forecast shown in Figure~\ref{fig:naive_density_forecast}.
+  where $Y_t$ represents the time series value at time $t$, $\epsilon$ is a white noise
+  parameter and $\phi$ and $\theta$ are coefficients determined by the Kalman filter. 
+  With knowledge of the transition probabilities and the dynamic behavior of each
+  state described by Equation~\ref{eqn:arma}, I can forecast solute time series orders of 
+  magnitude longer than with molecular simulations.
+
+%  Density forecasting can provide
+%  predictions based on properties of a time series without any knowledge
+%  of the physical interactions leading to those properties.
+
+%  \begin{wrapfigure}{l}{0.6\textwidth}
+%  \centering
+%  \vspace{-0.75cm}
+%  \includegraphics[width=\linewidth]{correlograms.pdf}
+%  \caption{Correlograms of $z_t$ reveal dependence for all 4 powers of 
+%  $(z - \overline{z})$.}\label{fig:correlograms}
+%  \vspace{-0.5cm}
+%  \end{wrapfigure}
+
+%With density forecasting, one can instead 
+%  compile the hop length and magnitude between each time step 
+%  (Figure~\ref{fig:first_order_difference}) into a probability density
+%  like that shown in Figure~\ref{fig:hop_density}. As a first attempt, 
+%  one could randomly draw from this distribution in order to construct
+%  a time series like that shown in Figure~\ref{fig:naive_density_forecast}.
+
+%  One can test how well a time series of hop lengths, $h_t$, is described by the 
+%  hop density, $p(h)$, in Figure~\ref{fig:hop_density} using the probability
+%  integral transform:~\cite{diebold_evaluating_1998}
+%  \begin{equation}
+%  z_t = \int_{-\infty}^{h_t} p(u) du
+%  \label{eqn:pit}
+%  \end{equation}
+%  Generally, one uses the first half of a time series, or in-sample data, to
+%  create $p(h)$ and applies Equation~\ref{eqn:pit} to the second half of
+%  the time series, or out-sample data. If the distribution of $z_t$ values
+%  is uniform, then the cumulative distribution function of $p(h)$ has been
+%  sampled uniformly by the out-sample data and there is evidence that the 
+%  time series is well-described by $p(h)$. Using the out-sample data from 
+%  Figure~\ref{fig:density_forecast}, we observe a uniform distribution of
+%  $z_t$ values (Figure~\ref{fig:z_histogram}).
+
+%  However, it is also necessary to look for correlations in $z_t$. Diebold
+%  et al. found that examination of the correlograms of $(z - \overline{z})$,
+%  $(z - \overline{z})^2$, $(z - \overline{z})^3$ and $(z - \overline{z})^4$,
+%  which represent dependence of the mean, variance, skewness and kurtosis 
+%  respectively, are adequate to identify potentially sophisticated and 
+%  nonlinear forms of past dependence.~\cite{diebold_evaluating_1998} Continuing
+%  with our example above, the correlograms of $z_t$ shown in Figure~\ref{fig:correlograms} 
+%  exhibit serial dependence for all powers of $(z - \overline{z})$. Our 
+%  time series exhibits dependence on its past values, a feature that was 
+%  not included in the forecast shown in Figure~\ref{fig:naive_density_forecast}.
   %This likely explains the qualitative difference in the time series of 
@@
 
-  Going forward, I will need to incorporate previous dependence in the 
-  form of a conditional density forecast with the form $p(h|\Omega_t)$ where
-  $\Omega_t$ incorporates past hop lengths and radial distances from
-  the pore center. These types of autoregressive models have been widely
-  studied in the context of economics, but are still well-suited for 
-  application to solute transport.~\cite{hamilton_time_1994}
+%  Going forward, I will need to incorporate previous dependence in the 
+%  form of a conditional density forecast with the form $p(h|\Omega_t)$ where
+%  $\Omega_t$ incorporates past hop lengths and radial distances from
+%  the pore center. These types of autoregressive models have been widely
+%  studied in the context of economics, but are still well-suited for 
+%  application to solute transport.~\cite{hamilton_time_1994}
 
@@
 
-  Paralleling our work on the H\textsubscript{II} phase, my first task towards
+  Paralleling my work on the H\textsubscript{II} phase, my first task towards
   this objective was to build a suitable unit cell representation of the 
-  Q\textsubscript{I} phase. Unfortunately, the true space group of the Q\textsubscript{I} phase that we
-  are studying is unknown. Experimental diffraction has narrowed down the 
-  possible bicontinuous cubic configurations to the Ia3d and Pn3m space groups. 
+  Q\textsubscript{I} phase. Unfortunately, the true space group of the 
+  Q\textsubscript{I} phase that we are studying is unknown. Experimental 
+  diffraction has narrowed down the possible bicontinuous cubic 
+  configurations to the Ia3d and Pn3m space groups.~\cite{pindzola_cross-linked_2003}
   Therefore, we will build both types of unit cells and search for clues that
@@
   I have developed a procedure that can build both Ia3d and Pn3m unit cells.
-  To our knowledge, nobody has ever built an atomistic bicontinuous cubic 
-  phase system without the aid of self-assembly. Self-assembly can be a long
-  process, especially for fully atomistic systems. Instead, we used known
-  analytical equations that describe the surface of these systems in order 
-  to place monomers into a unit cell. Monomers are placed perpendicular to
-  the surface in random locations that don't overlap. One can control the 
-  pore size by translating monomers perpendicular to the surface at the 
-  point where they are attached.
+  To our knowledge, nobody has ever built an atomistic molecular model of 
+  a bicontinuous cubic phase system. Some systems have been created by 
+  allowing coarse grained representations to self-assemble over long 
+  timescales.~\cite{mondal_self-assembly_2013} However, self-assembly
+  can be a long process, especially for fully atomistic systems, where it
+  might take multiple orders of magnitude longer than what we can 
+  reasonably simulate. Instead, I use analytical equations that describe
+  the surface of these systems in order to place monomers into a unit cell.~\cite{benedicto_bicontinuous_1997}
+  Monomers are placed perpendicular to the surface in random locations 
+  that don't overlap. One can control the pore size by translating monomers
+  perpendicular to the surface at the point where they are attached.
 
@@
   this might not work due to the known similarity of Ia3d and Pn3m XRD 
-  patterns. %cite
+  patterns.
 
@@
   challenge will be adapting my techniques to the more complex pore geometry
-  of the Q\textsubscript{I} phase, however I expect that main conclusions
+  of the Q\textsubscript{I} phase, however I expect that the main conclusions
   will not deviate far from those of the H\textsubscript{II} phase since
-  the chemical environments within the nanopores are qualitatively similar.. We may be 
-  able to identify which space group is correct if there are significantly
-  different transport properties between systems.
-
-%BJC: not sure how much more detail to include. Can go into a lot. Have to expand box and slowly compress. Add glycerol iteratively until there are no gaps.
+  the chemical environments within the nanopores are qualitatively similar.
+
+  The experimental performance of Q\textsubscript{I} phase membranes has been
+  studied far more extensively than that of the H\textsubscript{II} phase. 
+  Therefore, I may be able to identify which space group is correct if
+  one system exhibits experimentally inconsistent transport properties and one
+  does not. I can attempt to replicate the trends in the results of the separation
+  studies performed by Dischinger et al.~\cite{dischinger_application_2017} If
+  I can match the experimental trends, then there is a good chance that I can
+  use my molecular model to offer an explanation for the complex behavior described
+  in their work (see first paragraph of Section~\ref{section:objectives}).
+
+  %MRS2: emphasize comparison to experiments more here, based on what they have done, and what they will do; outline how you will compare to those experiments.
 

### 2019-06-17 LLC_Membranes/analysis/correlation_function.py
New figures and modifications for response to reviewers

@@ -124,7 +124,7 @@ class Correlation(object):
             print('Trajectory loaded')
 
         if atoms is None:
-            if res is None:
+            if res is None:  # better to raise an exception
                 sys.exit("You must specify either a group of atoms or residue. Neither have been provided therefore "
                          "I can't do anything")
 

### 2019-06-17 LLC_Membranes/analysis/hop_location.py

@@ -122,7 +122,7 @@ class HopLocation(System):
 
         :return tuple containing : (mean hop length in the pore, std in pore, mean out of pore, std out of pore)
         """
-        print(r)
+
         self.r = np.array(self.r)
 
         # flatten list
@@ -201,4 +201,4 @@ if __name__ == "__main__":
 
     #hops.regional_hop_lengths(0.75)
 
-    hops.plot_hop_locations(show=True, cmap_max=cmax, colormap=args.colormap, bins=args.bins)
+    #hops.plot_hop_locations(show=True, cmap_max=cmax, colormap=args.colormap, bins=args.bins)

### 2019-06-17 Ben_Manuscripts/transport/response_to_reviewers.tex
Response to reviewers

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{xr}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}

\externaldocument[S-]{Supporting_Information}
\externaldocument[M-]{Final_Draft}

\begin{document}

\graphicspath{{./figures/}}

\begin{center}
\textbf{Response to reviewers: Chemically Selective Transport in a Cross-linked 
H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane} \\
Authors: Benjamin J. Coscia and Michael R. Shirts
\end{center}

We thank the reviewers for carefully reading over our manuscript and providing
helpful comments. We have taken the suggestions into consideration and made
appropriate revisions to the manuscript document. All changes to the text have
been documented below. In cases where we modified the text we included the 
original text (denoted by ``Original text:") followed by the new text (denoted by
``New text:").

\section*{Response to Reviewer 1}

\begin{enumerate}

    \item \begin{quote} \textit{The manuscript, "Chemically Selective Transport 
    in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane,"
    is an interesting effort that provides solid and never-before-developed insights
    into how structure and chemistry impact separations in an important new class of
    membrane materials. In particular, the ability to focus on and explain in a 
    rather complete manner that complex mechanisms that lead to results that are 
    below the Stokes-Einstein limit is impressive.  While somewhat verbose at times, 
    the manuscript is communicated in a clear manner, and it should be of interest 
    to a number of researchers in the field. As such, publication is recommended after
    the following minor points are addressed by the manuscript.} 
    \end{quote}

    Author reply: We thank the reviewer for their positive impression and feedback 
    and address their specific concerns below.

    \item \begin{quote}
    \textit{The explanation regarding the transport of water molecules in the tail 
    region relative to water molecules in the pore region for the 5\% (by weight) 
    water system that occurs in the paragraph that begins at the end of page 20 is
    rather unsatisfying. While certain statistics are pointed to, there is not a 
    full explanation provided here. Expanding this point in order would strengthen
    the manuscript.}
    \end{quote}

    Author reply: We thank the reviewer for pushing us to strengthen our description
    of tail water transport in the 5 wt\% water system, as our point could be 
    confusing without proper explanation.

    Original text: ``In the 5 wt\% water system, water molecules that spend the majority
    of their time in the distal tail region have MSDs slightly higher than those of water
    molecules close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
    compared to 1.2 nm$^2$ outside the distal tails. This anomaly is likely a consequence
    of lower density in the distal tails relative to the pores, leading to faster diffusion
    in the tails, as well as slowed diffusion of water molecules in the pores via hydrogen 
    bonds with other water molecules and association with sodium ions. Water molecules are 
    less likely to hydrogen bond with each other while in the distal tail region since they
    are interspersed between chains, while those in the pores stay in close proximity to 
    each other. We observed about 9 times more hydrogen bonding between water molecules 
    near the pore center versus those in the distal tail region. Additionally, an average 
    of 65\% of water molecules in the pores of the 5 wt\% water system are associated
    with a sodium ion each frame compared to 44\% in the 10 wt\% water system. There is a
    negligible amount of hydrogen bonds between water molecules and monomer head groups.

    New text: ``In the 5 wt\% water system, water molecules that spend the majority of their 
	time in the distal tail region have MSDs slightly higher than those of water molecules
	close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
	compared to 1.2 nm$^2$ outside the distal tails. The reason for this anomaly is twofold. 
	First, monomer head groups are concentrated about 0.2 nm closer to the pore centers
	in the 5 wt\% versus the 10 wt\% water system (see Figure~\ref{M-fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water
	which results in more frequent collisions between water molecules and relatively immobile 
	monomer head groups. Second, the diffusion of water molecules is slowed via hydrogen
	bonds with other water molecules and association with sodium ions. Notably, there is a 
	negligible number of hydrogen bonds between water molecules and monomer head groups.
    The 95th percentile lifetime of hydrogen bonds between water molecules located near the
	pore center is 2.1 ns in the 5 wt\% system compared to 0.5 ns in the 10 wt\% system. 
	However, since we only saved simulation output every 0.5 ns, it is likely that the 
	true hydrogen bond lifetimes in the 10 wt\% system are smaller than this value. 
	With regard to sodium ions, more frequent and longer periods of association
	with water molecules helps to drive down water's MSD. An average of 65\% of water 
	molecules in the pores of the 5 wt\% water system associate with a sodium ion each
	frame compared to 44\% in the 10 wt\% water system. There are about half as many water
	molecules in the 5 wt\% water system which allows a larger fraction of them to associate
	with sodium ions. The lifetime of associations between sodium ions and water is 7.5 ns
	and 3.0 ns in 5 and 10 wt\% water systems respectively.  ``

    \item \begin{quote}
    \textit{The final paragraph of the conclusions of the manuscript ends on a blunt, and 
    somewhat pessimistic, note. That is, there is no doubt that there are complicated 
    interactions that will occur in many membrane separations, and that it is not always 
    easy to predict beforehand what the results will be. However, the strategy outlined 
    by this effort provides at least a footing by which to attack certain problems. This
    work provides atomistic modeling that does more than just allow one to think critically
    about nanostructured membranes. In fact, one might argue that one does not necessarily
    need such complex computational powers to think critically about nanostructured 
    membranes. Instead, one might argue that these kinds of efforts provide insights that
    would not necessarily be obvious from simple "chemical intuition" points of view that 
    are typically relied upon by many membrane scientists. As such, it might be useful to
    highlight where this effort provided insights that were not necessarily obvious as the
    end of the manuscript. This might serve as a means by which to entice experimentalist
    to incorporate these kinds of efforts into their own work such that the pace at which
    discoveries are made by the entire community is increased.}
    \end{quote}

    Author reply: We thank the reviewer for encouraging us to strengthen our conclusions and
    to end on a more positive note. We have modified our final paragraph with this in mind 
    and to emphasize that these types of studies are necessary to identify transport behavior
    that might not be obvious based solely on intuition.

    Original text: ``The findings here are likely too complex to point towards a clear 
    design of an optimal LLC membrane for a particular separation. This work does demonstrate
    that there is a large range of solute-membrane interactions resulting from the
    chemically complex and inhomogeneous LLC membrane structure. The varying chemical 
    functionality of the solutes themselves gives rise to an immense diversity of transport 
    behavior. This behavior suggests that a large range of chemical selectivities may be 
    possible in self-assembled nanoporous membranes. Atomistic modeling gives us the 
    opportunity to observe these interactions at the molecular scale, at least approximately,
    so that we can think more critically about nanostructured membrane design.''

    New text: ``Our work demonstrates that one cannot rely solely on chemical intuition while 
    designing LLC membranes for particular separations. The complex interplay between the
    inhomogeneous membrane structure, solute size and solute functionality leads to a variety of
    solute-membrane interactions, of which many are quite subtle. For example, association
    between polar groups and ions is seldom mentioned in the literature, but we could not give a
    complete mechanistic explanation of observed transport behavior without its consideration. 
    The interactions we observed, along with those that may arise in alternative self-assembled
    nanoporous membranes, can lead to an immense diversity of transport behavior which suggests
    that a large range of chemical selectivities may be possible. Atomistic molecular modeling
    may be the best hope of uncovering the dominant mechanisms that will inspire and accelerate
    novel design by experimentalists.''

\end{enumerate}

\section*{Response to Reviewer 2}

\begin{enumerate}

	\item \begin{quote} \textit{Using all-atom classical molecular dynamics (MD) simulations,
	the authors examined the transport properties of water, sodium ions and a total of 20 
	small polar solutes in a model lyotropic liquid crystal (LLC) membrane, specifically the
	hexagonal HII phase formed by the liquid crystal monomer Na-GA3C11. This is a very 
	detailed and brilliantly done molecular simulation study, where the data was carefully 
	analyzed to provide molecular-level insights about these systems that will be very 
	useful to experimentalists working with this type of membrane for water purification 
	purposes. I only have the following minor comments: }\end{quote}

	Author reply: We thank the reviewer for the kind assessment of our work. We address their
	comments below.

	\item \begin{quote}

	\textit{The water model used by the authors was not explicitly mentioned in Section 2 
	of the paper. From the Results section it is inferred that they used the TIP3P water model.
	The authors should explicitly mention their choice of water model in Section 2, and 
	justify this choice.}

	\end{quote}

	Author reply: We thank the reviewer for pointing out that we are missing this essential detail.
	We have added the following text to section 2.1 of the main text:

	New text: ``We simulated water molecules using the TIP3P water model because it is 
    computationally efficient and reasonably reproduces water's physical properties
    at 300K, the temperature of our simulations.``

  	We also added the following citation in support of our justification:

  	Mahoney, M. W.; Jorgensen, W. L. A Five-Site Model for Liquid Water and the Reproduction
  	of the Density Anomaly by Rigid, Nonpolarizable Potential Functions. J. Chem. Phys. 2000, 
  	112, 8910–8922

    \item \begin{quote}

    \textit{The Methods section should contain more details about the model membranes, for 
    example the length of the pores in the z-direction, the range of pore sizes (I understand
    they vary with water content), and the range of distances between the center of adjacent pores.}

    \end{quote}

    Author reply: We thank the reviewer for this suggestion. We agree that it would be useful
    to our readers if we included more details about our models. We have added the following 
    text to Section 2.2 of our Methods.

    %BJC: not sure what else to include.  Don't want to say anything about pore size
    %BJC: density is about the same 
    New text: ``The equilibrated unit cells have different geometries depending on water content. 
    The average distance between pores is 4.15 +/- 0.08 nm and 4.41 +/- 0.07 nm
    in the 5 and 10 wt\% water systems respectively. The length of the pores, accounting
    for tortuosity (see Section~\ref{M-method:rdfs}), is 9.03 +/- 0.12 nm and 8.07 +/- 0.11
    nm in the 5 and 10 wt\% water systems respectively.''  
    % BJC: not sure what if anything to say about difference in lengths of pores (which is roughly
    % equivalent to the box dimension in the z-direction). My guess is that when monomers don't 
    % stack directly on top of each other, they can pack tighter in the z-direction. When there
    % is more water, they are more disordered and can move away or closer to the pore center which
    % facilitates that packing. The RDF of head groups in the 10 wt% versus 5 wt% is broader (density
    % at peak is lower) which supports this. But that kind of discussion isn't suitable for methods,
    % and I don't think it's really in the scope of the paper. Would just add more words.

    We elected to not include pore sizes because its definition is ambiguous. There is not a 
    hard partition between the pore and tails. Rather, there is a gradual transition from 
    the hydrophilic to hydrophobic region. The approximate size of the pore region and the 
    boundaries we defined are addressed later in the methods and throughout the results and 
    discussion section.

    \item \begin{quote}

    \textit{I think most of the text related to preparation of the model systems (Section S2, 
    Supporting Information), should be moved into the Methods section of the paper. I believe 
    these simulation setup details are important to researchers working with somewhat similar 
    systems.}

    \end{quote}

    Author reply: We thank the reviewer for their suggestion. We've edited Section 2.2 of the main
    text to include a consolidated discussion of the data and analysis presented in Section S2, 
    while leaving the full discussion in Section S2.

    Old text: `` We observed that some water partitions into the distal tail region of our system and therefore
	built our initial configurations with water in both regions, close to the expected
	equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
	Information). We define the distal tail region to be ca. 1.5 nm from the pore
	center based on the minimum in the radial distribution function of water
	(see Section~\ref{M-method:rdfs}). The amount of water present in the distal tail region
	may or may not be experimentally consistent but it is necessary for our results to be 
	thermodynamically consistent; otherwise, water would slowly leak from the pore into the
	tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
	until the appropriate amount of water fit in the pores after running the GROMACS command
	\texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
	in random locations with a short energy minimization between each insertion. When 
	studying transport of water in the pores, we limited the calculations to water molecules
	that spent greater than 95\% of their time outside of the distal tail region. We 
	justify this decision with better context in Section~\ref{M-section:transport_water_sodium}.

    First, we equilibrated the initial configuration using the `wet' equilibration procedure 
	described in our previous work. Then we cross-linked the equilibrated solvated 
	configuration using the cross-linking procedure also described in our previous 
    work.''

    New text: `` We initially attempted to equilibrate our system with water by allowing water
	molecules to naturally penetrate the membrane from a water bath separating
	periodic images of the system in the $z$-direction. We allowed a dry, previously
	equilibrated system to further equilibrate in coexistence with a 3 nm-thick 
	(in the $z$-direction) layer of water. Although the water appears to equilibrate
	after 1000 ns of simulation, the density of water along the pore axis
	is close to zero at the membrane center, implying that there is a kinetic
	barrier to water filling the pores which we will be unable to overcome using
	conventional simulations. See Section~\ref{S-section:water_content_equil} of the
	Supporting Information for an expanded explanation and supporting figures.

	We observed water enters into the distal tail region of our system. We define the 
	distal tail region to be ca. 1.5 nm from the pore center based on the minimum in 
	the radial distribution function of water (see Section~\ref{M-method:rdfs}). Therefore
	we aimed to build our initial configurations with water in both regions, close to
	the expected equilibrium partition. The final amount of water present in the distal
	tail region may or may not be experimentally consistent but it is necessary for our
	results to be thermodynamically consistent; otherwise, water would slowly leak 
	from the pore into the tail region over several hundred nanoseconds.

	To determine the approximate ratio of water in the pores to tails, we equilibrated 4 systems
	where we initially placed water in the pores and in the tails in addition to a water
	reservoir between periodic images. We filled the pores with water by running the 
	GROMACS command \texttt{gmx solvate} on our initial configuration followed by the 
	removal of any water molecules placed in the distal tail region. This method requires
	that we vary the initial pore radius since the vacant space dictates the pore's 
	water content. We then placed a defined number of water molecules into the distal tail
	region one at a time with a short energy minimization between each insertion.
	We chose to test systems with initial pore radii of 5, 6, 7 and 8 \AA~with tail and 
	pore water compositions given in Table~\ref{table:water_content}. We found that 
	systems started with more water in the pores than tails tended to equilibrate relatively
	quickly with an approximate ratio of 3 water molecules in the pores to 2 in the tails.

    % BJC: could go back in supporting
    \begin{table}[!htb]
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
    \hline
    5                 &        5.67       &     1.09          \\
    6                 &        2.88       &     2.38          \\
    7                 &        1.91       &     4.12          \\
    8                 &        2.78       &     6.00          \\
    \hline
    \end{tabular}
    \caption{We chose a diverse combination of initial pore and tail water
    contents in order to study its effect on equilibrium water
    content.}\label{table:water_content}
    \end{table}

    \begin{figure}[!htb]
    \centering
    \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
    \caption{5 wt \%}\label{fig:5wt_offset_equil}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
    \caption{10 wt \%}\label{fig:10wt_offset_equil}
    \end{subfigure}
    \caption{We created solvated systems with one third of the total water
	  initially placed in the tail region. (a) With 5 wt \% total water, the water
	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
	  ns, with $\sim$ 69 \% of the total water in the
	  pores.}\label{fig:solvation_equilibration}
    \end{figure}

    We removed the water reservoir and allowed the pore and tail water
    contents to equilibrate with 5 and 10 wt\% total water with a 3:2 ratio
    of pore to tail water. We considered the water content
    equilibrated once the water contents plateaued. The 5 wt\% system did
    not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
    while the 10 wt \% water system equilibrated within the first 100 ns of 
    simulation (Figure~\ref{fig:10wt_offset_equil}).
    The equilibrated pores contain 72 \% and 69 \% of the total water in the
    5 and 10 wt \% systems respectively. We cross-linked the equilibrated 
    solvated systems, then allowed them to equilibrate further for 100 ns. 
    The water contents in each region does not change significantly in either case 
    (see Figure~\ref{S-fig:xlinked_solvation_equilibration} of the Supporting Information).
    The `wet' equilibration and cross-linking procedures follow
    the methods outlined in our previous work.''

\end{enumerate}

\end{document}

### 2019-06-17 Ben_Manuscripts/transport/Final_Draft.tex
Final draft of paper with reviewer comments incorporated

--- 2019-05-08 Ben_Manuscripts/transport/Draft.tex
@@
 
-  \subsection{Solute Parameterization}\label{method:parameterization}
+  \subsection{Molecule Parameterization}\label{method:parameterization}
 
@@
 
+  We simulated water molecules using the TIP3P water model because it is 
+  computationally efficient and reasonably reproduces water's physical properties
+  at 300K, the temperature of our simulations.~\cite{mahoney_five-site_2000}
+
   \subsection{System Setup}\label{method:system_setup}
@@
 
-  We observed that some water partitions into the distal tail region of our system and therefore
-  built our initial configurations with water in both regions, close to the expected
-  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
-  Information). We define the distal tail region to be ca. 1.5 nm from the pore
-  center based on the minimum in the radial distribution function of water
-  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
-  may or may not be experimentally consistent but it is necessary for our results to be 
-  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
-  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
-  until the appropriate amount of water fit in the pores after running the GROMACS command
-  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
-  in random locations with a short energy minimization between each insertion. When 
-  studying transport of water in the pores, we limited the calculations to water molecules
-  that spent greater than 95\% of their time outside of the distal tail region. We 
-  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
-  %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)
-  %BJC3: added reference to later section. 
-  %MRS3: We probably need to mention the amount of water there is; 40% is in the tail.
-We should probably discuss density; that because of the larger tail volume, the density is about 1/X in the distal region than in the pore.
-
-  We equilibrated an initial solvated configuration before adding solutes. First, we 
-  equilibrated the initial configuration using the `wet' equilibration procedure 
-  described in our previous work. Then we cross-linked the equilibrated solvated 
-  configuration using the cross-linking procedure also described in our previous 
-  work.~\cite{coscia_understanding_2019}
+  We initially attempted to equilibrate our system with water by allowing water
+  molecules to naturally penetrate the membrane from a water bath separating
+  periodic images of the system in the $z$-direction. We allowed a dry, previously
+  equilibrated system to further equilibrate in coexistence with a 3 nm-thick 
+  (in the $z$-direction) layer of water. Although the water appears to equilibrate
+  after 1000 ns of simulation, the density of water along the pore axis
+  is close to zero at the membrane center, implying that there is a kinetic
+  barrier to water filling the pores which we will be unable to overcome using
+  conventional simulations. See Section~\ref{S-section:water_content_equil} of the
+  Supporting Information for an expanded explanation and supporting figures.
+
+  We observed that water enters into the distal tail region of our system. We define the 
+  distal tail region to be 1.5 nm from the pore center based on the minimum in 
+  the radial distribution function of water (see Section~\ref{method:rdfs}). Therefore,
+  we aimed to build our initial configurations with water in both regions, close to
+  the expected equilibrium partition. The final amount of water present in the distal
+  tail region may or may not be experimentally consistent but it is necessary for our
+  results to be thermodynamically consistent; otherwise, water would slowly leak 
+  from the pore into the tail region over several hundred nanoseconds.
+
+  To determine the approximate ratio of water in the pores to tails, we equilibrated 4 systems
+  where we initially placed water in the pores and in the tails in addition to a water
+  reservoir between periodic images. We filled the pores with water by running the 
+  GROMACS command \texttt{gmx solvate} on our initial configuration followed by the 
+  removal of any water molecules placed in the distal tail region. This method requires
+  that we vary the initial pore radius since the vacant space dictates the pore's 
+  water content. We then placed a defined number of water molecules into the distal tail
+  region one at a time with a short energy minimization between each insertion.
+  We chose to test systems with initial pore radii of 5, 6, 7 and 8 \AA~with tail and 
+  pore water compositions given in Table~\ref{table:water_content}. We found that 
+  systems started with more water in the pores than tails tended to equilibrate relatively
+  quickly with an approximate ratio of 3 water molecules in the pores to 2 in the tails.
+
+  % BJC: could go back in supporting
+  \begin{table}[!htb]
+  \centering
+  \begin{tabular}{|c|c|c|}
+  \hline
+  Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
+  \hline
+  5                 &        5.67       &     1.09          \\
+  6                 &        2.88       &     2.38          \\
+  7                 &        1.91       &     4.12          \\
+  8                 &        2.78       &     6.00          \\
+  \hline
+  \end{tabular}
+  \caption{We chose a diverse combination of initial pore and tail water
+  contents in order to study its effect on equilibrium water
+  content.}\label{table:water_content}
+  \end{table}
+
+  \begin{figure}[!htb]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
+  \caption{5 wt \%}\label{fig:5wt_offset_equil}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
+  \caption{10 wt \%}\label{fig:10wt_offset_equil}
+  \end{subfigure}
+  \caption{We created solvated systems with one third of the total water
+	  initially placed in the tail region. (a) With 5 wt \% total water, the water
+	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
+	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
+	  ns, with $\sim$ 69 \% of the total water in the
+	  pores.}\label{fig:solvation_equilibration}
+  \end{figure}
+
+  We removed the water reservoir and allowed the pore and tail water
+  contents to equilibrate with 5 and 10 wt\% total water with a 3:2 ratio
+  of pore to tail water. We considered the water content
+  equilibrated once the water contents plateaued. The 5 wt\% system did
+  not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
+  while the 10 wt \% water system equilibrated within the first 100 ns of 
+  simulation (Figure~\ref{fig:10wt_offset_equil}).
+  The equilibrated pores contain 72 \% and 69 \% of the total water in the
+  5 and 10 wt \% systems respectively. We cross-linked the equilibrated 
+  solvated systems, then allowed them to equilibrate further for 100 ns. 
+  The water contents in each region does not change significantly in either case 
+  (see Figure~\ref{S-fig:xlinked_solvation_equilibration} of the Supporting
+  Information). The `wet' equilibration and cross-linking procedures follow
+  the methods outlined in our previous work.~\cite{coscia_understanding_2019}
+
+%  We observed that some water partitions into the distal tail region of our system and therefore
+%  built our initial configurations with water in both regions, close to the expected
+%  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
+%  Information). We define the distal tail region to be ca. 1.5 nm from the pore
+%  center based on the minimum in the radial distribution function of water
+%  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
+%  may or may not be experimentally consistent but it is necessary for our results to be 
+%  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
+%  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
+%  until the appropriate amount of water fit in the pores after running the GROMACS command
+%  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
+%  in random locations with a short energy minimization between each insertion. When 
+%  studying transport of water in the pores, we limited the calculations to water molecules
+%  that spent greater than 95\% of their time outside of the distal tail region. We 
+%  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
+
+%  We fully equilibrated an initial solvated configuration before adding solutes. First, we 
+%  equilibrated the initial configuration using the `wet' equilibration procedure 
+%  described in our previous work. Then we cross-linked the equilibrated solvated 
+%  configuration using the cross-linking procedure also described in our previous 
+%  work.~\cite{coscia_understanding_2019}
+
+  %BJC: Addressing reviewer 2
+  The equilibrated unit cells have different geometries depending on water content. 
+  The average distance between pores is 4.15 +/- 0.08 nm and 4.41 +/- 0.07 nm
+  in the 5 and 10 wt\% water systems respectively. The length of the pores, accounting
+  for tortuosity (see Section~\ref{method:rdfs}), is 9.03 +/- 0.12 nm and 8.07 +/- 0.11
+  nm in the 5 and 10 wt\% water systems respectively.
 
@@
 
-  %MRS2: could potentially make these sections bulleted list, rather than full subsections.
   \subsection{Mean Squared Displacement}\label{method:MSD}
@@
   close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
-  compared to 1.2 nm$^2$ outside the distal tails. This anomaly is likely a 
-  consequence of lower density in the distal tails relative to the pores,
-  leading to faster diffusion in the tails,
-  as well as slowed diffusion of water molecules in the pores via hydrogen bonds
-  with other water molecules and association with sodium ions. Water molecules 
-  are less likely to hydrogen bond with each other while in the distal tail 
-  region since they are interspersed between chains, while those in 
-  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
-  hydrogen bonding between water molecules near the pore center versus those in 
-  the distal tail region. Additionally, an average of 65\% of water molecules in
-  the pores of the 5 wt\% water system are associated with a sodium ion each frame
-  compared to 44 \% in the 10 wt\% water system. There is a negligible amount of
-  hydrogen bonds between water molecules and monomer head groups.
+  compared to 1.2 nm$^2$ outside the distal tails. The reason for this anomaly is twofold. 
+  First, monomer head groups are concentrated about 0.2 nm closer to the pore centers
+  in the 5 wt\% versus the 10 wt\% water system (see Figure~\ref{fig:component_densities})
+  which results in more frequent collisions between water molecules and relatively immobile 
+  monomer head groups. Second, the diffusion of water molecules is slowed via hydrogen
+  bonds with other water molecules and association with sodium ions. Notably, there is a 
+  negligible number of hydrogen bonds between water molecules and monomer head groups. 
+  The 95th percentile lifetime of hydrogen bonds between water molecules located near the
+  pore center is 2.1 ns in the 5 wt\% system compared to 0.5 ns in the 10 wt\% system. 
+  However, since we only saved simulation output every 0.5 ns, it is likely that the 
+  true hydrogen bond lifetimes in the 10 wt\% system are smaller than this value. 
+  With regard to sodium ions, more frequent and longer periods of association
+  with water molecules helps to drive down water's MSD. An average of 65\% of water 
+  molecules in the pores of the 5 wt\% water system associate with a sodium ion each
+  frame compared to 44\% in the 10 wt\% water system. There are about half as many water
+  molecules in the 5 wt\% water system which allows a larger fraction of them to associate
+  with sodium ions. The lifetime of associations between sodium ions and water is 7.5 ns
+  and 3.0 ns in 5 and 10 wt\% water systems respectively.
+
+%  Water molecules 
+%  are less likely to hydrogen bond with each other while in the distal tail region 
+%  since they are interspersed between chains, while those in the pores stay in close
+%  proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
+%  hydrogen bonding between water molecules near the pore center versus those in 
+%  the distal tail region.
+
+%  is anomaly is likely a 
+%  consequence of lower density in the distal tails relative to the pores,
+%  leading to faster diffusion in the tails,
+%  as well as slowed diffusion of water molecules in the pores via hydrogen bonds
+%  with other water molecules and association with sodium ions. Water molecules 
+%  are less likely to hydrogen bond with each other while in the distal tail 
+%  region since they are interspersed between chains, while those in 
+%  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
+%  hydrogen bonding between water molecules near the pore center versus those in 
+%  the distal tail region. Additionally, an average of 65\% of water molecules in
+%  the pores of the 5 wt\% water system are associated with a sodium ion each frame
+%  compared to 44 \% in the 10 wt\% water system. There is a negligible amount of
+%  hydrogen bonds between water molecules and monomer head groups.
 
@@
 
-  The findings here are likely too complex to point towards a clear design of an 
-  optimal LLC membrane for a particular separation. This work does demonstrate
-  that there is a large range of solute-membrane interactions resulting from the
-  chemically complex and inhomogeneous LLC membrane structure. The varying 
-  chemical functionality of the solutes themselves gives rise to an immense diversity of
-  transport behavior. This behavior suggests that a large range of chemical 
-  selectivities may be possible in self-assembled nanoporous membranes. Atomistic
-  modeling gives us the opportunity to observe these interactions at the molecular
-  scale, at least approximately, so that we can think more critically about 
-  nanostructured membrane design.
+%  The findings here are likely too complex to point towards a clear design of an 
+%  optimal LLC membrane for a particular separation. This work does demonstrate
+%  that there is a large range of solute-membrane interactions resulting from the
+%  chemically complex and inhomogeneous LLC membrane structure. The varying 
+%  chemical functionality of the solutes themselves gives rise to an immense diversity of
+%  transport behavior. This behavior suggests that a large range of chemical 
+%  selectivities may be possible in self-assembled nanoporous membranes. Atomistic
+%  modeling gives us the opportunity to observe these interactions at the molecular
+%  scale, at least approximately, so that we can think more critically about 
+%  nanostructured membrane design.
+
+  Our work demonstrates that one cannot rely solely on chemical intuition while 
+  designing LLC membranes for particular separations. The complex interplay between the
+  inhomogeneous membrane structure, solute size and solute functionality leads to a variety of
+  solute-membrane interactions, of which many are quite subtle. For example, association
+  between polar groups and ions is seldom mentioned in the literature, but we could not give a
+  complete mechanistic explanation of observed transport behavior without its consideration. 
+  The interactions we observed, along with those that may arise in alternative self-assembled
+  nanoporous membranes, can lead to an immense diversity of transport behavior which suggests
+  that a large range of chemical selectivities may be possible. Atomistic molecular modeling
+  may be the best hope of uncovering the dominant mechanisms that will inspire and accelerate
+  novel design by experimentalists.
 

### 2019-06-21 Ben_Manuscripts/transport/response_to_reviewers.tex
comments on letter.

@@
 
+    %MRS: I'd leave out the text that stays the same (like the first sentence). 
     Original text: ``In the 5 wt\% water system, water molecules that spend the majority
@@
 	in the 5 wt\% versus the 10 wt\% water system (see Figure~\ref{M-fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water
+        %MRS: rather than saying there are more frequent collisions, I'd just say that it leaves less space, 
+        %restricting the motion of the water.   
         which results in more frequent collisions between water molecules and relatively immobile 
-	monomer head groups. Second, the diffusion of water molecules is slowed via hydrogen
+	monomer head groups. 
+        %MRS: but this next ``Second,'' doesn't explain why this slows things down more in 5%; just because the concentration of ions is higher?  But the concentration of water molecules is lower. 
+        Second, the diffusion of water molecules is slowed via hydrogen
 	bonds with other water molecules and association with sodium ions. Notably, there is a 
@@
 	true hydrogen bond lifetimes in the 10 wt\% system are smaller than this value. 
+        %MRS: hmm the organization says: 2 effects, x and y.  Here is more about X. Here is more about Y. 
+        %MRS to make clear what is being talked about where, it might be better to say: ``There are 2 effects. Here is X, here is Y.''
+        %MRS: don't start with dependent clauses.  This logic makes sense, but the above one doesn't so much, 
+        %MRS: because it's not made clear why the H-bonds are lasting longer (clearly, if they are lasting longer, MSD will go up). 
 	With regard to sodium ions, more frequent and longer periods of association
@@
     to end on a more positive note. We have modified our final paragraph with this in mind 
-    and to emphasize that these types of studies are necessary to identify transport behavior
-    that might not be obvious based solely on intuition.
+    and to emphasize that these types of studies are 
+    %necessary to identify
+    very valuable in identifying
+    transport behavior
+    that might not be obvious based solely on intuition
+    %MRS: added
+    or bulk scale experiments.
 
@@
     New text: ``Our work demonstrates that one cannot rely solely on chemical intuition while 
-    designing LLC membranes for particular separations. The complex interplay between the
+    designing LLC membranes for particular separations. 
+    %MRS5: Hmm.  Still not quite: we want to communicate ``experiment PLUS
+    %simulations!'' not ``experiments are not enough''. How about something more like this?
+    %``Our work demonstrates that there are important, atomistic features of nanostructed, self-assembled materials 
+    % that molecular simulation can play a key role in elucidating''
+    The complex interplay between the
     inhomogeneous membrane structure, solute size and solute functionality leads to a variety of
@@
     complete mechanistic explanation of observed transport behavior without its consideration. 
-    The interactions we observed, along with those that may arise in alternative self-assembled
-    nanoporous membranes, can lead to an immense diversity of transport behavior which suggests
-    that a large range of chemical selectivities may be possible. Atomistic molecular modeling
-    may be the best hope of uncovering the dominant mechanisms that will inspire and accelerate
+    %MRS: is there a second example you can put in as well?
+    The interactions we observed, along with those that may arise in 
+    %MRS: simpler
+    %alternative 
+    other
+    self-assembled
+    nanoporous membranes, 
+    %can lead to an substantial
+    have the potential to produce an immense 
+    diversity of transport behavior, 
+    %which suggests
+    suggesting
+    that a 
+    %MRS: 
+    previously unexplored range
+    %large range 
+    of chemical selectivities may be possible. Atomistic molecular modeling
+    %MRS: maybe a bit overkill
+    %may be the best hope of
+    is likely to be highly useful in
+    uncovering 
+    %the dominant 
+    important 
+    mechanisms that will inspire and accelerate
     novel design by experimentalists.''
@@
     at 300K, the temperature of our simulations.``
-
+        %MRS3: TIP-4P is pretty close in efficiency, and TIP3P is only mediocre in bulk water properties  I would probably say that TIP3P was used because it is the water model that GAFF and other AMBER family parameters were optmized with.
+TIP3P also diffuses faster than experimental water, which is both a negative (can't compare absolute diffusion) and positive (things happen faster).
   	We also added the following citation in support of our justification:
 
+        %MRS: that's the TIP5P paper, though . . . did you mean to cite it?
   	Mahoney, M. W.; Jorgensen, W. L. A Five-Site Model for Liquid Water and the Reproduction
@@
 
+    %MRS: I would actually put this argument more clearly in the paper
+    %- if the reviewer missed it, readers will as well.  If it's in
+    %there already, I would emphasize it, and then mention here where
+    %it was added, and cite the previous paper - it was one of the main messages of that paper.
     We elected to not include pore sizes because its definition is ambiguous. There is not a 
     hard partition between the pore and tails. Rather, there is a gradual transition from 
-    the hydrophilic to hydrophobic region. The approximate size of the pore region and the 
+    the hydrophilic to hydrophobic region. 
+    The approximate size of the pore region and the 
     boundaries we defined are addressed later in the methods and throughout the results and 
@@
 	barrier to water filling the pores which we will be unable to overcome using
-	conventional simulations. See Section~\ref{S-section:water_content_equil} of the
-	Supporting Information for an expanded explanation and supporting figures.
+	conventional simulations. See Section~\ref{S-section:water_content_equil} 
+        %MRS: will need to get the references working using xr or manually for the letter.
+        of the Supporting Information for an expanded explanation and supporting figures.
 
+        %MRS: might want to make it clear that this below is a separate feature, observed in 
+        %different simulations than the ones above.
 	We observed water enters into the distal tail region of our system. We define the 
@@
 	removal of any water molecules placed in the distal tail region. This method requires
-	that we vary the initial pore radius since the vacant space dictates the pore's 
+	that we vary the 
+        %MRS: is ``initial pore radius'' a good phrase to use, since we are fighting against the idea of 
+        % well-defined pore radii?  ``monomer starting radius?''
+        initial pore radius since the vacant space dictates the pore's 
 	water content. We then placed a defined number of water molecules into the distal tail
@@
     % BJC: could go back in supporting
+    % MRS: I could go either way.
     \begin{table}[!htb]
@@
 
+    %MRS: is this figure below moving to the front?  I think may be it still is more of a supporting figure.
     \begin{figure}[!htb]

### 2019-06-24 Ben_Manuscripts/transport/response_to_reviewers.tex
Refinement

@@
 
-    %MRS: I'd leave out the text that stays the same (like the first sentence). 
-    Original text: ``In the 5 wt\% water system, water molecules that spend the majority
-    of their time in the distal tail region have MSDs slightly higher than those of water
-    molecules close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
-    compared to 1.2 nm$^2$ outside the distal tails. This anomaly is likely a consequence
-    of lower density in the distal tails relative to the pores, leading to faster diffusion
-    in the tails, as well as slowed diffusion of water molecules in the pores via hydrogen 
+    Original text: ``This anomaly is likely a consequence of lower density in the
+    distal tails relative to the pores, leading to faster diffusion in the tails,
+    as well as slowed diffusion of water molecules in the pores via hydrogen 
     bonds with other water molecules and association with sodium ions. Water molecules are 
@@
 
-    New text: ``In the 5 wt\% water system, water molecules that spend the majority of their 
-	time in the distal tail region have MSDs slightly higher than those of water molecules
-	close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
-	compared to 1.2 nm$^2$ outside the distal tails. The reason for this anomaly is twofold. 
-	First, monomer head groups are concentrated about 0.2 nm closer to the pore centers
-	in the 5 wt\% versus the 10 wt\% water system (see Figure~\ref{M-fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water
-        %MRS: rather than saying there are more frequent collisions, I'd just say that it leaves less space, 
+    %BJC2: restructured into single reason, since longer association times are a 
+    % consequence of crowding.
+    %New text: ``The reason for this anomaly is twofold. First, monomer head groups are
+    New text: ``This behavior is likely due to the much more crowded pore environment
+    in the 5 wt\% versus the 10 wt\% water system. Monomer head groups are
+    concentrated about 2\AA closer to the pore centers in the 5 wt\% versus the 10 
+    wt\% water system (see Figure~\ref{M-fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water
+    % MRS: rather than saying there are more frequent collisions, I'd just say that it leaves less space, 
     %restricting the motion of the water.   
-        which results in more frequent collisions between water molecules and relatively immobile 
-	monomer head groups. 
-        %MRS: but this next ``Second,'' doesn't explain why this slows things down more in 5%; just because the concentration of ions is higher?  But the concentration of water molecules is lower. 
-        Second, the diffusion of water molecules is slowed via hydrogen
-	bonds with other water molecules and association with sodium ions. Notably, there is a 
-	negligible number of hydrogen bonds between water molecules and monomer head groups.
+    which leaves less space for water molecules and restricts their movement among the 
+    relatively immobile monomer head groups. 
+    % MRS: but this next ``Second,'' doesn't explain why this slows things down more in 5%; 
+    % just because the concentration of ions is higher?  But the concentration of water molecules is lower. 
+%    This slow-down, caused by the high energetic barrier to diffusion, is exacerbated by 
+%    simultaneously enhancing the favorability of interactions between water and monomer
+%    components. 
+    The consequently high energetic barrier to diffusion enhances the favorability of 
+    associative interactions between water and monomer components.
+%    As a consequence of this crowding, the diffusion of water molecules is even 
+%    further slowed by longer periods of association with monomer components. %hydrogen bonds with other water molecules and association with sodium ions. 
+%    Notably, there is a negligible number of hydrogen bonds between water molecules and monomer head groups.
     The 95th percentile lifetime of hydrogen bonds between water molecules located near the
@@
     %MRS: because it's not made clear why the H-bonds are lasting longer (clearly, if they are lasting longer, MSD will go up). 
-	With regard to sodium ions, more frequent and longer periods of association
-	with water molecules helps to drive down water's MSD. An average of 65\% of water 
-	molecules in the pores of the 5 wt\% water system associate with a sodium ion each
-	frame compared to 44\% in the 10 wt\% water system. There are about half as many water
-	molecules in the 5 wt\% water system which allows a larger fraction of them to associate
-	with sodium ions. The lifetime of associations between sodium ions and water is 7.5 ns
-	and 3.0 ns in 5 and 10 wt\% water systems respectively.  ``
+	Additionally, there are more frequent and longer periods of association between water
+	and sodium ions. An average of 65\% of water molecules in the pores of the 5 wt\% water
+	system associate with a sodium ion each frame compared to 44\% in the 10 wt\% water system.
+	There are about half as many water molecules in the 5 wt\% water system which allows a 
+	larger fraction of them to associate with sodium ions. The lifetime of associations
+	between sodium ions and water is 7.5 ns and 3.0 ns in 5 and 10 wt\% water systems respectively.``
 
@@
     to end on a more positive note. We have modified our final paragraph with this in mind 
-    and to emphasize that these types of studies are 
-    %necessary to identify
-    very valuable in identifying
-    transport behavior
-    that might not be obvious based solely on intuition
-    %MRS: added
-    or bulk scale experiments.
+    and to emphasize that these types of studies are very valuable in identifying transport
+    behavior that might not be obvious based solely on intuition or bulk scale experiments.
 
@@
 
-    New text: ``Our work demonstrates that one cannot rely solely on chemical intuition while 
-    designing LLC membranes for particular separations. 
-    %MRS5: Hmm.  Still not quite: we want to communicate ``experiment PLUS
-    %simulations!'' not ``experiments are not enough''. How about something more like this?
-    %``Our work demonstrates that there are important, atomistic features of nanostructed, self-assembled materials 
-    % that molecular simulation can play a key role in elucidating''
-    The complex interplay between the
-    inhomogeneous membrane structure, solute size and solute functionality leads to a variety of
-    solute-membrane interactions, of which many are quite subtle. For example, association
-    between polar groups and ions is seldom mentioned in the literature, but we could not give a
-    complete mechanistic explanation of observed transport behavior without its consideration. 
-    %MRS: is there a second example you can put in as well?
-    The interactions we observed, along with those that may arise in 
-    %MRS: simpler
-    %alternative 
-    other
-    self-assembled
-    nanoporous membranes, 
-    %can lead to an substantial
-    have the potential to produce an immense 
-    diversity of transport behavior, 
-    %which suggests
-    suggesting
-    that a 
-    %MRS: 
-    previously unexplored range
-    %large range 
-    of chemical selectivities may be possible. Atomistic molecular modeling
-    %MRS: maybe a bit overkill
-    %may be the best hope of
-    is likely to be highly useful in
-    uncovering 
-    %the dominant 
-    important 
-    mechanisms that will inspire and accelerate
-    novel design by experimentalists.''
+    % BJC: incorporated MRS thesis suggestion
+    New text: ``Our work demonstrates that there are important, atomistic features of nanostructed, 
+    self-assembled materials that molecular simulation can play a key role in elucidating.
+    The complex interplay between the inhomogeneous membrane structure, solute size and 
+    solute functionality leads to a variety of solute-membrane interactions, of which many
+    are quite subtle. For example, association between polar groups and ions is seldom 
+    mentioned in the literature, but we could not give a complete mechanistic explanation
+    of observed transport behavior without its consideration. 
+    % MRS: is there a second example you can put in as well?
+    % BJC: A second example  (water in the tails):
+    We also observed that water and solutes partition into the tails, an area previously 
+    assumed to be devoid of solutes, which offers another route towards selectivity.
+    The interactions we observed, along with those that may arise in other self-assembled
+    nanoporous membranes, have the potential to produce an immense diversity of transport
+    behavior, suggesting that a previously unexplored range of chemical selectivities may
+    be possible. Atomistic molecular modeling is likely to be highly useful in uncovering 
+    important mechanisms that will inspire and accelerate novel design by experimentalists.''
 
@@
 
-	New text: ``We simulated water molecules using the TIP3P water model because it is 
-    computationally efficient and reasonably reproduces water's physical properties
-    at 300K, the temperature of our simulations.``
+	New text: ``We simulated water molecules using the TIP3P water model because it 
+	has been shown to sufficiently reproduce physical properties well in lipid membrane
+	system where other residues were parameterized with GAFF.''
+%    computationally efficient and reasonably reproduces water's physical properties
+%    at 300K, the temperature of our simulations.``
+
     %MRS3: TIP-4P is pretty close in efficiency, and TIP3P is only mediocre in bulk water properties  I would probably say that TIP3P was used because it is the water model that GAFF and other AMBER family parameters were optmized with.
 TIP3P also diffuses faster than experimental water, which is both a negative (can't compare absolute diffusion) and positive (things happen faster).
+    %BJC2: I don't see any mention of water models in the GAFF paper. Maybe I'm overlooking something. 
+    % Instead, I cited a study of TIP3P in a lipid membrane system where the lipids were parameterized with
+    % GAFF.
+
   	We also added the following citation in support of our justification:
@@
     %MRS: that's the TIP5P paper, though . . . did you mean to cite it?
-  	Mahoney, M. W.; Jorgensen, W. L. A Five-Site Model for Liquid Water and the Reproduction
-  	of the Density Anomaly by Rigid, Nonpolarizable Potential Functions. J. Chem. Phys. 2000, 
-  	112, 8910–8922
+    %BJC2: I used it because it has a comparison between physical properties exhibited by different water models inlcuding tip3p. 
+%  	Mahoney, M. W.; Jorgensen, W. L. A Five-Site Model for Liquid Water and the Reproduction
+%  	of the Density Anomaly by Rigid, Nonpolarizable Potential Functions. J. Chem. Phys. 2000, 
+%  	112, 8910–8922
+
+    Jójárt, Balázs, and Tamás A. Martinek. “Performance of the General Amber Force Field
+    in Modeling Aqueous POPC Membrane Bilayers.” Journal of Computational Chemistry 28, 
+    no. 12 (2007): 2051–58. https://doi.org/10.1002/jcc.20748.
 
@@
 
-    %BJC: not sure what else to include.  Don't want to say anything about pore size
-    %BJC: density is about the same 
-    New text: ``The equilibrated unit cells have different geometries depending on water content. 
-    The average distance between pores is 4.15 +/- 0.08 nm and 4.41 +/- 0.07 nm
+    %BJC2: incorporated point about pore size
+    New text: ``The equilibrated unit cells have different geometries depending on water
+    content. The average distance between pores is 4.15 +/- 0.08 nm and 4.41 +/- 0.07 nm
     in the 5 and 10 wt\% water systems respectively. The length of the pores, accounting
     for tortuosity (see Section~\ref{M-method:rdfs}), is 9.03 +/- 0.12 nm and 8.07 +/- 0.11
-    nm in the 5 and 10 wt\% water systems respectively.''  
+    nm in the 5 and 10 wt\% water systems respectively. The approximate size of the pore
+    region increases with water content (see Section~\ref{M-section:membrane_components}), 
+    however we did not quantify the pore radius because its definition is ambiguous. As
+    described in our previous work, there is not a hard partition between the pore and tail
+    regions.~\cite{coscia_understanding_2019} Rather, there is a gradual transition from 
+    the hydrophilic to hydrophobic region.''
+
     % BJC: not sure what if anything to say about difference in lengths of pores (which is roughly
@@
     %it was added, and cite the previous paper - it was one of the main messages of that paper.
-    We elected to not include pore sizes because its definition is ambiguous. There is not a 
-    hard partition between the pore and tails. Rather, there is a gradual transition from 
-    the hydrophilic to hydrophobic region. 
-    The approximate size of the pore region and the 
-    boundaries we defined are addressed later in the methods and throughout the results and 
-    discussion section.
+    %BJC2: moved into paragraph above
+%    We elected to not include pore sizes because its definition is ambiguous. There is not a 
+%    hard partition between the pore and tails. Rather, there is a gradual transition from 
+%    the hydrophilic to hydrophobic region. 
+%    The approximate size of the pore region and the 
+%    boundaries we defined are addressed later in the methods and throughout the results and 
+%    discussion section.
 
@@
     %MRS: will need to get the references working using xr or manually for the letter.
+    %BJC2: will ensure this before sending off
     of the Supporting Information for an expanded explanation and supporting figures.
 
-        %MRS: might want to make it clear that this below is a separate feature, observed in 
-        %different simulations than the ones above.
+    % MRS: might want to make it clear that this below is a separate feature, observed in 
+    % different simulations than the ones above.
+    % BJC2: I'm actually talking about the same simulation since I observed water in the 
+    % tails of the water bath simulations as well. That's what inspired the other systems.
 	We observed water enters into the distal tail region of our system. We define the 
@@
     % well-defined pore radii?  ``monomer starting radius?''
-        initial pore radius since the vacant space dictates the pore's 
+    % BJC2: good point
+    monomer starting radius since the vacant space dictates the pore's 
 	water content. We then placed a defined number of water molecules into the distal tail
@@
 	We chose to test systems with initial pore radii of 5, 6, 7 and 8 \AA~with tail and 
-	pore water compositions given in Table~\ref{table:water_content}. We found that 
+	pore water compositions given in Table~\ref{S-table:water_content}. We found that 
 	systems started with more water in the pores than tails tended to equilibrate relatively
@@
 
-    % BJC: could go back in supporting
+    % BJC: could go back in supporting.
     % MRS: I could go either way.
-    \begin{table}[!htb]
-    \centering
-    \begin{tabular}{|c|c|c|}
-    \hline
-    Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
-    \hline
-    5                 &        5.67       &     1.09          \\
-    6                 &        2.88       &     2.38          \\
-    7                 &        1.91       &     4.12          \\
-    8                 &        2.78       &     6.00          \\
-    \hline
-    \end{tabular}
-    \caption{We chose a diverse combination of initial pore and tail water
-    contents in order to study its effect on equilibrium water
-    content.}\label{table:water_content}
-    \end{table}
+    % BJC2: moved to supporting. I don't think it adds much value here.
+%    \begin{table}[!htb]
+%    \centering
+%    \begin{tabular}{|c|c|c|}
+%    \hline
+%    Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
+%    \hline
+%    5                 &        5.67       &     1.09          \\
+%    6                 &        2.88       &     2.38          \\
+%    7                 &        1.91       &     4.12          \\
+%    8                 &        2.78       &     6.00          \\
+%    \hline
+%    \end{tabular}
+%    \caption{We chose a diverse combination of initial pore and tail water
+%    contents in order to study its effect on equilibrium water
+%    content.}\label{table:water_content}
+%    \end{table}
 
     %MRS: is this figure below moving to the front?  I think may be it still is more of a supporting figure.
-    \begin{figure}[!htb]
-    \centering
-    \begin{subfigure}{0.45\textwidth}
-    \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
-    \caption{5 wt \%}\label{fig:5wt_offset_equil}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-    \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
-    \caption{10 wt \%}\label{fig:10wt_offset_equil}
-    \end{subfigure}
-    \caption{We created solvated systems with one third of the total water
-	  initially placed in the tail region. (a) With 5 wt \% total water, the water
-	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
-	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
-	  ns, with $\sim$ 69 \% of the total water in the
-	  pores.}\label{fig:solvation_equilibration}
-    \end{figure}
+    %BJC2: I agree, removed from main document. 
+%    \begin{figure}[!htb]
+%    \centering
+%    \begin{subfigure}{0.45\textwidth}
+%    \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
+%    \caption{5 wt \%}\label{fig:5wt_offset_equil}
+%    \end{subfigure}
+%    \begin{subfigure}{0.45\textwidth}
+%    \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
+%    \caption{10 wt \%}\label{fig:10wt_offset_equil}
+%    \end{subfigure}
+%    \caption{We created solvated systems with one third of the total water
+%	  initially placed in the tail region. (a) With 5 wt \% total water, the water
+%	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
+%	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
+%	  ns, with $\sim$ 69 \% of the total water in the
+%	  pores.}\label{fig:solvation_equilibration}
+%    \end{figure}
 
@@
     equilibrated once the water contents plateaued. The 5 wt\% system did
-    not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
+    not plateau until $\sim$ 600 ns 
     while the 10 wt \% water system equilibrated within the first 100 ns of 
-    simulation (Figure~\ref{fig:10wt_offset_equil}).
-    The equilibrated pores contain 72 \% and 69 \% of the total water in the
+    simulation (see Figure~\ref{S-fig:5wt_offset_equil} and Figure~\ref{S-fig:10wt_offset_equil} of
+    the Supporting Information). The equilibrated pores contain 72 \% and 69 \% of the total water in the
     5 and 10 wt \% systems respectively. We cross-linked the equilibrated 
@@
 
+\bibliographystyle{ieeetr}
+\bibliography{transport}
+
 \end{document}

### 2019-06-24 Ben_Manuscripts/transport/response_to_reviewers.tex
A couple of comments.

@@
     in the 5 wt\% versus the 10 wt\% water system. Monomer head groups are
-    concentrated about 2\AA closer to the pore centers in the 5 wt\% versus the 10 
+    concentrated about 2\AA~closer to the pore centers in the 5 wt\% versus the 10 
     wt\% water system (see Figure~\ref{M-fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water
@@
 	However, since we only saved simulation output every 0.5 ns, it is likely that the 
-	true hydrogen bond lifetimes in the 10 wt\% system are smaller than this value.
+	true hydrogen bond lifetimes in the 10 wt\% system are 
+        %MRS2: tweaked
+        %smaller
+        shorter
+        than this value.
     %MRS: hmm the organization says: 2 effects, x and y.  Here is more about X. Here is more about Y. 
@@
     The complex interplay between the inhomogeneous membrane structure, solute size and 
-    solute functionality leads to a variety of solute-membrane interactions, of which many
+    solute functionality leads to a variety of solute-membrane interactions, many of which
     are quite subtle. For example, association between polar groups and ions is seldom 
@@
 
-    %MRS3: TIP-4P is pretty close in efficiency, and TIP3P is only mediocre in bulk water properties  I would probably say that TIP3P was used because it is the water model that GAFF and other AMBER family parameters were optmized with.
+    %MRS: TIP-4P is pretty close in efficiency, and TIP3P is only mediocre in bulk water properties  I would probably say that TIP3P was used because it is the water model that GAFF and other AMBER family parameters were optmized with.
 TIP3P also diffuses faster than experimental water, which is both a negative (can't compare absolute diffusion) and positive (things happen faster).
@@
     % GAFF.
+    %MRS: Gaff uses the same charge model and VDW types that AMBER does, which was parameterized to be compatible with TIP3P water.
 
@@
     %BJC2: I used it because it has a comparison between physical properties exhibited by different water models inlcuding tip3p. 
+    %MRS2: there have been a number of water model papers since then (look at TIP4P-Ew paper of Horn et al, OPC paper)
 %  	Mahoney, M. W.; Jorgensen, W. L. A Five-Site Model for Liquid Water and the Reproduction
@@
     the hydrophilic to hydrophobic region.''  
+    %MRS2: should also talk about where this is discussed in THIS paper.  We want to make sure people are 
+    % visualizing what we are imagining when reading this paper.
 

### 2019-06-24 Ben_Manuscripts/transport/response_to_reviewers.tex
Incorporated changes into final draft

@@
 
-    %BJC2: restructured into single reason, since longer association times are a 
-    % consequence of crowding.
-    %New text: ``The reason for this anomaly is twofold. First, monomer head groups are
     New text: ``This behavior is likely due to the much more crowded pore environment
@@
     wt\% water system (see Figure~\ref{M-fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water 
-    % MRS: rather than saying there are more frequent collisions, I'd just say that it leaves less space, 
-    %restricting the motion of the water.   
     which leaves less space for water molecules and restricts their movement among the 
-    relatively immobile monomer head groups. 
-    % MRS: but this next ``Second,'' doesn't explain why this slows things down more in 5%; 
-    % just because the concentration of ions is higher?  But the concentration of water molecules is lower. 
-%    This slow-down, caused by the high energetic barrier to diffusion, is exacerbated by 
-%    simultaneously enhancing the favorability of interactions between water and monomer
-%    components. 
-    The consequently high energetic barrier to diffusion enhances the favorability of 
-    associative interactions between water and monomer components.
-%    As a consequence of this crowding, the diffusion of water molecules is even 
-%    further slowed by longer periods of association with monomer components. %hydrogen bonds with other water molecules and association with sodium ions. 
-%    Notably, there is a negligible number of hydrogen bonds between water molecules and monomer head groups.
-    The 95th percentile lifetime of hydrogen bonds between water molecules located near the
-	pore center is 2.1 ns in the 5 wt\% system compared to 0.5 ns in the 10 wt\% system. 
-	However, since we only saved simulation output every 0.5 ns, it is likely that the 
-	true hydrogen bond lifetimes in the 10 wt\% system are 
-        %MRS2: tweaked
-        %smaller
-        shorter
-        than this value.
-    %MRS: hmm the organization says: 2 effects, x and y.  Here is more about X. Here is more about Y. 
-    %MRS to make clear what is being talked about where, it might be better to say: ``There are 2 effects. Here is X, here is Y.''
-    %MRS: don't start with dependent clauses. This logic makes sense, but the above one doesn't so much, 
-    %MRS: because it's not made clear why the H-bonds are lasting longer (clearly, if they are lasting longer, MSD will go up). 
-	Additionally, there are more frequent and longer periods of association between water
-	and sodium ions. An average of 65\% of water molecules in the pores of the 5 wt\% water
-	system associate with a sodium ion each frame compared to 44\% in the 10 wt\% water system.
+    relatively immobile monomer head groups. The consequently high energetic barrier 
+    to diffusion enhances the favorability of associative interactions between water
+    and monomer components. The 95th percentile lifetime of hydrogen bonds between 
+    water molecules located near the pore center is 2.1 ns in the 5 wt\% system compared
+    to 0.5 ns in the 10 wt\% system. However, since we only saved simulation output 
+    every 0.5 ns, it is likely that the true hydrogen bond lifetimes in the 10 wt\% 
+    system are shorter than this value. Additionally, there are more frequent and longer
+    periods of association between water and sodium ions. An average of 65\% of water 
+    molecules in the pores of the 5 wt\% water system associate with a sodium ion each
+    frame compared to 44\% in the 10 wt\% water system.
 	There are about half as many water molecules in the 5 wt\% water system which allows a 
@@
 
-    % BJC: incorporated MRS thesis suggestion
     New text: ``Our work demonstrates that there are important, atomistic features of nanostructed, 
@@
     mentioned in the literature, but we could not give a complete mechanistic explanation
-    of observed transport behavior without its consideration. 
-    % MRS: is there a second example you can put in as well?
-    % BJC: A second example  (water in the tails):
-    We also observed that water and solutes partition into the tails, an area previously 
-    assumed to be devoid of solutes, which offers another route towards selectivity.
+    of observed transport behavior without its consideration. We also observed that water
+    and solutes partition into the tails, an area previously assumed to be devoid of solutes,
+    which offers another route towards selectivity.
     The interactions we observed, along with those that may arise in other self-assembled
@@
 	New text: ``We simulated water molecules using the TIP3P water model because it 
-	has been shown to sufficiently reproduce physical properties well in lipid membrane
-	system where other residues were parameterized with GAFF.''
+	because it is the water model that GAFF and other AMBER family parameters were optmized with.''
 %    computationally efficient and reasonably reproduces water's physical properties
@@
 
-  	We also added the following citation in support of our justification:
+  	We added the following citation in support of our justification:
 
-    %MRS: that's the TIP5P paper, though . . . did you mean to cite it?
-    %BJC2: I used it because it has a comparison between physical properties exhibited by different water models inlcuding tip3p. 
-    %MRS2: there have been a number of water model papers since then (look at TIP4P-Ew paper of Horn et al, OPC paper)
-%  	Mahoney, M. W.; Jorgensen, W. L. A Five-Site Model for Liquid Water and the Reproduction
-%  	of the Density Anomaly by Rigid, Nonpolarizable Potential Functions. J. Chem. Phys. 2000, 
-%  	112, 8910–8922
-
-    Jójárt, Balázs, and Tamás A. Martinek. “Performance of the General Amber Force Field
-    in Modeling Aqueous POPC Membrane Bilayers.” Journal of Computational Chemistry 28, 
-    no. 12 (2007): 2051–58. https://doi.org/10.1002/jcc.20748.
+    Florová, Petra, Petr Sklenovský, Pavel Banáš, and Michal Otyepka. “Explicit Water 
+    Models Affect the Specific Solvation and Dynamics of Unfolded Peptides While the 
+    Conformational Behavior and Flexibility of Folded Peptides Remain Intact.” Journal 
+    of Chemical Theory and Computation 6, no. 11 (November 9, 2010): 3569–79. https://doi.org/10.1021/ct1003687.
 
@@
     described in our previous work, there is not a hard partition between the pore and tail
-    regions.~\cite{coscia_understanding_2019} Rather, there is a gradual transition from 
-    the hydrophilic to hydrophobic region.''  
+    regions. Rather, there is a gradual transition from the hydrophilic to hydrophobic region.''  
     %MRS2: should also talk about where this is discussed in THIS paper.  We want to make sure people are 
     % visualizing what we are imagining when reading this paper.
-
-    % BJC: not sure what if anything to say about difference in lengths of pores (which is roughly
-    % equivalent to the box dimension in the z-direction). My guess is that when monomers don't 
-    % stack directly on top of each other, they can pack tighter in the z-direction. When there
-    % is more water, they are more disordered and can move away or closer to the pore center which
-    % facilitates that packing. The RDF of head groups in the 10 wt% versus 5 wt% is broader (density
-    % at peak is lower) which supports this. But that kind of discussion isn't suitable for methods,
-    % and I don't think it's really in the scope of the paper. Would just add more words.
-
-    %MRS: I would actually put this argument more clearly in the paper
-    %- if the reviewer missed it, readers will as well.  If it's in
-    %there already, I would emphasize it, and then mention here where
-    %it was added, and cite the previous paper - it was one of the main messages of that paper.
-    %BJC2: moved into paragraph above
-%    We elected to not include pore sizes because its definition is ambiguous. There is not a 
-%    hard partition between the pore and tails. Rather, there is a gradual transition from 
-%    the hydrophilic to hydrophobic region. 
-%    The approximate size of the pore region and the 
-%    boundaries we defined are addressed later in the methods and throughout the results and 
-%    discussion section.
 
@@
 
-    New text: `` We initially attempted to equilibrate our system with water by allowing water
+    New text: ``We initially attempted to equilibrate our system with water by allowing water
 	molecules to naturally penetrate the membrane from a water bath separating
@@
 	conventional simulations. See Section~\ref{S-section:water_content_equil} 
-    %MRS: will need to get the references working using xr or manually for the letter.
-    %BJC2: will ensure this before sending off
     of the Supporting Information for an expanded explanation and supporting figures.
 
-    % MRS: might want to make it clear that this below is a separate feature, observed in 
-    % different simulations than the ones above.
-    % BJC2: I'm actually talking about the same simulation since I observed water in the 
-    % tails of the water bath simulations as well. That's what inspired the other systems.
 	We observed water enters into the distal tail region of our system. We define the 
@@
 	removal of any water molecules placed in the distal tail region. This method requires
-	that we vary the 
-    %MRS: is ``initial pore radius'' a good phrase to use, since we are fighting against the idea of 
-    % well-defined pore radii?  ``monomer starting radius?''
-    % BJC2: good point
-    monomer starting radius since the vacant space dictates the pore's 
+	that we vary the monomer starting radius since the vacant space dictates the pore's 
 	water content. We then placed a defined number of water molecules into the distal tail
@@
 
-    % BJC: could go back in supporting.
-    % MRS: I could go either way.
-    % BJC2: moved to supporting. I don't think it adds much value here.
-%    \begin{table}[!htb]
-%    \centering
-%    \begin{tabular}{|c|c|c|}
-%    \hline
-%    Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
-%    \hline
-%    5                 &        5.67       &     1.09          \\
-%    6                 &        2.88       &     2.38          \\
-%    7                 &        1.91       &     4.12          \\
-%    8                 &        2.78       &     6.00          \\
-%    \hline
-%    \end{tabular}
-%    \caption{We chose a diverse combination of initial pore and tail water
-%    contents in order to study its effect on equilibrium water
-%    content.}\label{table:water_content}
-%    \end{table}
-
-    %MRS: is this figure below moving to the front?  I think may be it still is more of a supporting figure.
-    %BJC2: I agree, removed from main document. 
-%    \begin{figure}[!htb]
-%    \centering
-%    \begin{subfigure}{0.45\textwidth}
-%    \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
-%    \caption{5 wt \%}\label{fig:5wt_offset_equil}
-%    \end{subfigure}
-%    \begin{subfigure}{0.45\textwidth}
-%    \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
-%    \caption{10 wt \%}\label{fig:10wt_offset_equil}
-%    \end{subfigure}
-%    \caption{We created solvated systems with one third of the total water
-%	  initially placed in the tail region. (a) With 5 wt \% total water, the water
-%	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
-%	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
-%	  ns, with $\sim$ 69 \% of the total water in the
-%	  pores.}\label{fig:solvation_equilibration}
-%    \end{figure}
-
     We removed the water reservoir and allowed the pore and tail water
@@
     equilibrated once the water contents plateaued. The 5 wt\% system did
-    not plateau until $\sim$ 600 ns 
-    while the 10 wt \% water system equilibrated within the first 100 ns of 
+    not plateau until $\sim$ 600 ns while the 10 wt \% water system equilibrated within the first 100 ns of 
     simulation (see Figure~\ref{S-fig:5wt_offset_equil} and Figure~\ref{S-fig:10wt_offset_equil} of
@@
 
-\bibliographystyle{ieeetr}
-\bibliography{transport}
+%\bibliographystyle{ieeetr}
+%\bibliography{transport}
 

### 2019-06-24 Ben_Manuscripts/transport/Final_Draft.tex
Incorporated changes into final draft

@@
   \end{subfigure}
-  %MRS3: include a bit more description in the caption of what the system: This is the figure that provides the orientation to the readers of what they will be thinking about for the rest of the paper.
-  %BJC3: gave it another shot
   \caption{The H\textsubscript{II} phase formed by LLC monomer NaGA3C11 (a)
@@
 
-  We simulated water molecules using the TIP3P water model because it is 
-  computationally efficient and reasonably reproduces water's physical properties
-  at 300K, the temperature of our simulations.~\cite{mahoney_five-site_2000}
+  We simulated water molecules using the TIP3P water model because it because
+  it is the water model that GAFF and other AMBER family parameters were optmized 
+  with.~\cite{florova_explicit_2010} %~\cite{mahoney_five-site_2000}
 
@@
   barrier to water filling the pores which we will be unable to overcome using
-  conventional simulations. See Section~\ref{S-section:water_content_equil} of the
-  Supporting Information for an expanded explanation and supporting figures.
-
-  We observed that water enters into the distal tail region of our system. We define the 
-  distal tail region to be 1.5 nm from the pore center based on the minimum in 
-  the radial distribution function of water (see Section~\ref{method:rdfs}). Therefore,
+  conventional simulations. See Section~\ref{S-section:water_content_equil} 
+  of the Supporting Information for an expanded explanation and supporting figures.
+
+  We observed water enters into the distal tail region of our system. We define the 
+  distal tail region to be ca. 1.5 nm from the pore center based on the minimum in 
+  the radial distribution function of water (see Section~\ref{method:rdfs}). Therefore
   we aimed to build our initial configurations with water in both regions, close to
@@
   removal of any water molecules placed in the distal tail region. This method requires
-  that we vary the initial pore radius since the vacant space dictates the pore's 
+  that we vary the monomer starting radius since the vacant space dictates the pore's 
   water content. We then placed a defined number of water molecules into the distal tail
@@
   We chose to test systems with initial pore radii of 5, 6, 7 and 8 \AA~with tail and 
-  pore water compositions given in Table~\ref{table:water_content}. We found that 
+  pore water compositions given in Table~\ref{S-table:water_content}. We found that 
   systems started with more water in the pores than tails tended to equilibrate relatively
   quickly with an approximate ratio of 3 water molecules in the pores to 2 in the tails.
-
-  % BJC: could go back in supporting
-  \begin{table}[!htb]
-  \centering
-  \begin{tabular}{|c|c|c|}
-  \hline
-  Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
-  \hline
-  5                 &        5.67       &     1.09          \\
-  6                 &        2.88       &     2.38          \\
-  7                 &        1.91       &     4.12          \\
-  8                 &        2.78       &     6.00          \\
-  \hline
-  \end{tabular}
-  \caption{We chose a diverse combination of initial pore and tail water
-  contents in order to study its effect on equilibrium water
-  content.}\label{table:water_content}
-  \end{table}
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
-  \caption{5 wt \%}\label{fig:5wt_offset_equil}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
-  \caption{10 wt \%}\label{fig:10wt_offset_equil}
-  \end{subfigure}
-  \caption{We created solvated systems with one third of the total water
-	  initially placed in the tail region. (a) With 5 wt \% total water, the water
-	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
-	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
-	  ns, with $\sim$ 69 \% of the total water in the
-	  pores.}\label{fig:solvation_equilibration}
-  \end{figure}
 
@@
   equilibrated once the water contents plateaued. The 5 wt\% system did
-  not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
+  not plateau until $\sim$ 600 ns 
   while the 10 wt \% water system equilibrated within the first 100 ns of 
-  simulation (Figure~\ref{fig:10wt_offset_equil}).
-  The equilibrated pores contain 72 \% and 69 \% of the total water in the
+  simulation (see Figure~\ref{S-fig:5wt_offset_equil} and Figure~\ref{S-fig:10wt_offset_equil} of
+  the Supporting Information). The equilibrated pores contain 72 \% and 69 \% of the total water in the
   5 and 10 wt \% systems respectively. We cross-linked the equilibrated 
@@
   The water contents in each region does not change significantly in either case 
-  (see Figure~\ref{S-fig:xlinked_solvation_equilibration} of the Supporting
-  Information). The `wet' equilibration and cross-linking procedures follow
-  the methods outlined in our previous work.~\cite{coscia_understanding_2019}
+  (see Figure~\ref{S-fig:xlinked_solvation_equilibration} of the Supporting Information).
+  The `wet' equilibration and cross-linking procedures follow
+  the methods outlined in our previous work.
 
@@
 
-  %BJC: Addressing reviewer 2
-  The equilibrated unit cells have different geometries depending on water content. 
-  The average distance between pores is 4.15 +/- 0.08 nm and 4.41 +/- 0.07 nm
+  The equilibrated unit cells have different geometries depending on water
+  content. The average distance between pores is 4.15 +/- 0.08 nm and 4.41 +/- 0.07 nm
   in the 5 and 10 wt\% water systems respectively. The length of the pores, accounting
   for tortuosity (see Section~\ref{method:rdfs}), is 9.03 +/- 0.12 nm and 8.07 +/- 0.11
-  nm in the 5 and 10 wt\% water systems respectively.
+  nm in the 5 and 10 wt\% water systems respectively. The approximate size of the pore
+  region increases with water content (see Section~\ref{section:membrane_components}), 
+  however we did not quantify the pore radius because its definition is ambiguous. As
+  described in our previous work, there is not a hard partition between the pore and tail
+  regions.~\cite{coscia_understanding_2019} Rather, there is a gradual transition from 
+  the hydrophilic to hydrophobic region.
+
+%  The approximate size of the pore region and the 
+%    boundaries we defined are addressed later in the methods and throughout the results and 
+%    discussion section.
 
@@
 
-  % Changing pore radius does not change conclusion here.
+  % Changing does not change conclusion here.
   In the 5 wt\% water system, water molecules that spend the majority of their 
@@
   close to the pore center. The MSD of distal tail water molecules is 1.7 nm$^2$
-  compared to 1.2 nm$^2$ outside the distal tails. The reason for this anomaly is twofold. 
-  First, monomer head groups are concentrated about 0.2 nm closer to the pore centers
-  in the 5 wt\% versus the 10 wt\% water system (see Figure~\ref{fig:component_densities})
-  which results in more frequent collisions between water molecules and relatively immobile 
-  monomer head groups. Second, the diffusion of water molecules is slowed via hydrogen
-  bonds with other water molecules and association with sodium ions. Notably, there is a 
-  negligible number of hydrogen bonds between water molecules and monomer head groups. 
-  The 95th percentile lifetime of hydrogen bonds between water molecules located near the
-  pore center is 2.1 ns in the 5 wt\% system compared to 0.5 ns in the 10 wt\% system. 
-  However, since we only saved simulation output every 0.5 ns, it is likely that the 
-  true hydrogen bond lifetimes in the 10 wt\% system are smaller than this value. 
-  With regard to sodium ions, more frequent and longer periods of association
-  with water molecules helps to drive down water's MSD. An average of 65\% of water 
+  compared to 1.2 nm$^2$ outside the distal tails. This behavior is likely due to the
+  much more crowded pore environment in the 5 wt\% versus the 10 wt\% water system. 
+  Monomer head groups are concentrated about 2\AA~closer to the pore centers in the
+  5 wt\% versus the 10 wt\% water system (see Figure~\ref{fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water 
+  which leaves less space for water molecules and restricts their movement among the 
+  relatively immobile monomer head groups. The consequently high energetic barrier 
+  to diffusion enhances the favorability of associative interactions between water
+  and monomer components. The 95th percentile lifetime of hydrogen bonds between 
+  water molecules located near the pore center is 2.1 ns in the 5 wt\% system compared
+  to 0.5 ns in the 10 wt\% system. However, since we only saved simulation output 
+  every 0.5 ns, it is likely that the true hydrogen bond lifetimes in the 10 wt\% 
+  system are shorter than this value. Additionally, there are more frequent and longer
+  periods of association between water and sodium ions. An average of 65\% of water 
   molecules in the pores of the 5 wt\% water system associate with a sodium ion each
-  frame compared to 44\% in the 10 wt\% water system. There are about half as many water
-  molecules in the 5 wt\% water system which allows a larger fraction of them to associate
-  with sodium ions. The lifetime of associations between sodium ions and water is 7.5 ns
-  and 3.0 ns in 5 and 10 wt\% water systems respectively.
+  frame compared to 44\% in the 10 wt\% water system.There are about half as many water
+  molecules in the 5 wt\% water system which allows a larger fraction of them to 
+  associate with sodium ions. The lifetime of associations between sodium ions and 
+  water is 7.5 ns and 3.0 ns in 5 and 10 wt\% water systems respectively.
+
+%  The reason for this anomaly is twofold. 
+%  First, monomer head groups are concentrated about 0.2 nm closer to the pore centers
+%  in the 5 wt\% versus the 10 wt\% water system (see Figure~\ref{fig:component_densities})
+%  which results in more frequent collisions between water molecules and relatively immobile 
+%  monomer head groups. Second, the diffusion of water molecules is slowed via hydrogen
+%  bonds with other water molecules and association with sodium ions. Notably, there is a 
+%  negligible number of hydrogen bonds between water molecules and monomer head groups. 
+%  The 95th percentile lifetime of hydrogen bonds between water molecules located near the
+%  pore center is 2.1 ns in the 5 wt\% system compared to 0.5 ns in the 10 wt\% system. 
+%  However, since we only saved simulation output every 0.5 ns, it is likely that the 
+%  true hydrogen bond lifetimes in the 10 wt\% system are smaller than this value. 
+%  With regard to sodium ions, more frequent and longer periods of association
+%  with water molecules helps to drive down water's MSD. An average of 65\% of water 
+%  molecules in the pores of the 5 wt\% water system associate with a sodium ion each
+%  frame compared to 44\% in the 10 wt\% water system. There are about half as many water
+%  molecules in the 5 wt\% water system which allows a larger fraction of them to associate
+%  with sodium ions. The lifetime of associations between sodium ions and water is 7.5 ns
+%  and 3.0 ns in 5 and 10 wt\% water systems respectively.
 
@@
 
-  Our work demonstrates that one cannot rely solely on chemical intuition while 
-  designing LLC membranes for particular separations. The complex interplay between the
-  inhomogeneous membrane structure, solute size and solute functionality leads to a variety of
-  solute-membrane interactions, of which many are quite subtle. For example, association
-  between polar groups and ions is seldom mentioned in the literature, but we could not give a
-  complete mechanistic explanation of observed transport behavior without its consideration. 
-  The interactions we observed, along with those that may arise in alternative self-assembled
-  nanoporous membranes, can lead to an immense diversity of transport behavior which suggests
-  that a large range of chemical selectivities may be possible. Atomistic molecular modeling
-  may be the best hope of uncovering the dominant mechanisms that will inspire and accelerate
-  novel design by experimentalists.
+%  Our work demonstrates that one cannot rely solely on chemical intuition while 
+%  designing LLC membranes for particular separations. The complex interplay between the
+%  inhomogeneous membrane structure, solute size and solute functionality leads to a variety of
+%  solute-membrane interactions, of which many are quite subtle. For example, association
+%  between polar groups and ions is seldom mentioned in the literature, but we could not give a
+%  complete mechanistic explanation of observed transport behavior without its consideration. 
+%  The interactions we observed, along with those that may arise in alternative self-assembled
+%  nanoporous membranes, can lead to an immense diversity of transport behavior which suggests
+%  that a large range of chemical selectivities may be possible. Atomistic molecular modeling
+%  may be the best hope of uncovering the dominant mechanisms that will inspire and accelerate
+%  novel design by experimentalists.
+
+  Our work demonstrates that there are important, atomistic features of nanostructed, 
+  self-assembled materials that molecular simulation can play a key role in elucidating.
+  The complex interplay between the inhomogeneous membrane structure, solute size and 
+  solute functionality leads to a variety of solute-membrane interactions, many of which
+  are quite subtle. For example, association between polar groups and ions is seldom 
+  mentioned in the literature, but we could not give a complete mechanistic explanation
+  of observed transport behavior without its consideration. We also observed that water
+  and solutes partition into the tails, an area previously assumed to be devoid of solutes,
+  which offers another route towards selectivity. The interactions we observed, along 
+  with those that may arise in other self-assembled nanoporous membranes, have the 
+  potential to produce an immense diversity of transport behavior, suggesting that a 
+  previously unexplored range of chemical selectivities may be possible. Atomistic 
+  molecular modeling is likely to be highly useful in uncovering important mechanisms
+  that will inspire and accelerate novel design by experimentalists.
 

### 2019-06-25 Ben_Manuscripts/transport/Final_Draft.tex
Final revision

@@
   4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} Assuming that the pKa of
-  gallic acid is similar to NaGA3C11, it is possible for our sodium salted
+  gallic acid is similar to Na-GA3C11, it is possible for our sodium salted
   monomer to exist at the same time as protonated acetic acid. In any case, we
@@
   \end{subfigure}
-  \caption{The H\textsubscript{II} phase formed by LLC monomer NaGA3C11 (a)
+  \caption{The H\textsubscript{II} phase formed by LLC monomer Na-GA3C11 (a)
   consists of pores that are approximately straight (b) and packed hexagonally (c).
-  In both figures, water molecules that occupy the pores are colored blue, 
+  In both (b) and (c), water molecules that occupy the pores are colored blue, 
   the hydrophilic head groups of the LLC monomers are colored orange and all else is colored gray. 
@@
   We parameterized the interaction potential for the monomer and solutes using
-  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
+  the General AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
   Antechamber package \cite{wang_automatic_2006} shipped with
@@
 
-  We simulated water molecules using the TIP3P water model because it because
-  it is the water model that GAFF and other AMBER family parameters were optmized 
+  We simulated water molecules using the TIP3P water model because it is the
+  water model that GAFF and other AMBER family parameters have been optmized
   with.~\cite{florova_explicit_2010} %~\cite{mahoney_five-site_2000}
@@
 
-  We observed water enters into the distal tail region of our system. We define the 
-  distal tail region to be ca. 1.5 nm from the pore center based on the minimum in 
-  the radial distribution function of water (see Section~\ref{method:rdfs}). Therefore
-  we aimed to build our initial configurations with water in both regions, close to
-  the expected equilibrium partition. The final amount of water present in the distal
-  tail region may or may not be experimentally consistent but it is necessary for our
-  results to be thermodynamically consistent; otherwise, water would slowly leak 
-  from the pore into the tail region over several hundred nanoseconds.
-
-  To determine the approximate ratio of water in the pores to tails, we equilibrated 4 systems
-  where we initially placed water in the pores and in the tails in addition to a water
-  reservoir between periodic images. We filled the pores with water by running the 
-  GROMACS command \texttt{gmx solvate} on our initial configuration followed by the 
-  removal of any water molecules placed in the distal tail region. This method requires
-  that we vary the monomer starting radius since the vacant space dictates the pore's 
-  water content. We then placed a defined number of water molecules into the distal tail
-  region one at a time with a short energy minimization between each insertion.
-  We chose to test systems with initial pore radii of 5, 6, 7 and 8 \AA~with tail and 
-  pore water compositions given in Table~\ref{S-table:water_content}. We found that 
-  systems started with more water in the pores than tails tended to equilibrate relatively
-  quickly with an approximate ratio of 3 water molecules in the pores to 2 in the tails.
-
-  We removed the water reservoir and allowed the pore and tail water
-  contents to equilibrate with 5 and 10 wt\% total water with a 3:2 ratio
-  of pore to tail water. We considered the water content
-  equilibrated once the water contents plateaued. The 5 wt\% system did
-  not plateau until $\sim$ 600 ns 
-  while the 10 wt \% water system equilibrated within the first 100 ns of 
-  simulation (see Figure~\ref{S-fig:5wt_offset_equil} and Figure~\ref{S-fig:10wt_offset_equil} of
-  the Supporting Information). The equilibrated pores contain 72 \% and 69 \% of the total water in the
-  5 and 10 wt \% systems respectively. We cross-linked the equilibrated 
-  solvated systems, then allowed them to equilibrate further for 100 ns. 
-  The water contents in each region does not change significantly in either case 
-  (see Figure~\ref{S-fig:xlinked_solvation_equilibration} of the Supporting Information).
-  The `wet' equilibration and cross-linking procedures follow
-  the methods outlined in our previous work.
+  We observed that water enters into the distal tail region of our system. We
+  define the distal tail region to be ca. 1.5 nm from the pore center based on
+  the minimum in the radial distribution function of water (see
+  Section~\ref{method:rdfs}). Therefore we aimed to build our initial
+  configurations with water in both regions, close to the expected equilibrium
+  partition. The final amount of water present in the distal tail region may or
+  may not be experimentally consistent but it is necessary for our results to be
+  thermodynamically consistent; otherwise, water would slowly leak from the pore
+  into the tail region over several hundred nanoseconds.
+
+  To determine the approximate ratio of water in the pores to tails, we
+  equilibrated 4 systems where we initially placed water in the pores and in the
+  tails in addition to a water reservoir between periodic images. We filled the
+  pores of our initial configuraiton with water by running the GROMACS command
+  \texttt{gmx solvate} on our initial configuration followed by the removal of
+  any water molecules placed in the distal tail region. This method requires that
+  we vary the monomer starting radius since the vacant space dictates the pore's
+  water content. We then placed a defined number of water molecules into the
+  distal tail region one at a time with a short energy minimization between each
+  insertion. We chose to test systems with initial pore radii of 5, 6, 7 and 8
+  \AA~with tail and pore water compositions given in
+  Table~\ref{S-table:water_content}. We found that systems started with more
+  water in the pores than tails tended to equilibrate relatively quickly with an
+  approximate ratio of 3 water molecules in the pores to 2 in the tails.
+
+  We removed the water reservoir and allowed the pore and tail water contents
+  to equilibrate with 5 and 10 wt\% total water with a 3:2 ratio of pore to tail
+  water. We considered the water content equilibrated once the number of water
+  molecules in each region plateaued. The 5 wt\% system did not plateau until
+  $\sim$ 600 ns while the 10 wt \% water system equilibrated within the first 100
+  ns of simulation (see Figure~\ref{S-fig:5wt_offset_equil} and
+  Figure~\ref{S-fig:10wt_offset_equil} of the Supporting Information). The
+  equilibrated pores contain 72 \% and 69 \% of the total water in the 5 and 10
+  wt \% systems respectively. We cross-linked the equilibrated solvated systems,
+  then allowed them to equilibrate further for 100 ns. The water contents in
+  each region does not change significantly in either case (see
+  Figure~\ref{S-fig:xlinked_solvation_equilibration} of the Supporting
+  Information). The `wet' equilibration and cross-linking procedures follow the
+  methods outlined in our previous work.~\cite{coscia_understanding_2019}
 
@@
   furthest from the pore center (a \& c). Water concentration is highest in regions of
-  low monomer density regions (b \& d).}\label{fig:total_density}
+  low monomer density (b \& d).}\label{fig:total_density}
   \end{figure}
@@
   membrane constituents, water and sodium, in a system absent of any additional
-  solutes. We then present the general trends that we observe among the
+  solutes. We then present the general trends that we observe among 
   all other solutes studied.
@@
   much more crowded pore environment in the 5 wt\% versus the 10 wt\% water system. 
-  Monomer head groups are concentrated about 2\AA~closer to the pore centers in the
+  Monomer head groups are concentrated about 2~\AA~closer to the pore centers in the
   5 wt\% versus the 10 wt\% water system (see Figure~\ref{fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water 
@@
   also increases with the number of hydroxyl groups. In the most extreme case, all 
-  four hydroxyl groups of Ribose (n = 4) are involved in a hydrogen bond interaction
+  four hydroxyl groups of ribose (n = 4) are involved in a hydrogen bond interaction
   at the same time.}\label{fig:polyols}

### 2019-06-25 Ben_Manuscripts/transport/Supporting_Information.tex
Minor figure changes
New figures and modifications for response to reviewers
Formatted, addded affiliations and fixed title

@@
 \usepackage{xr}
+\usepackage{authblk}
 
-\externaldocument[M-]{Outline}
+\externaldocument[M-]{Final_Draft}
 
@@
 
-\title{Supporting Information: Chemically Selective Transport in a Cross-linked 
+\title{Supporting Information: Chemically Selective Transport in a Cross-Linked 
 H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
-\author{Benjamin J. Coscia \and Michael R. Shirts}
+\author[1]{Benjamin J. Coscia}
+\author[1]{Michael R. Shirts} 
+\date{E-mail: michael.shirts@colorado.edu}
+
+\affil[1]{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
 
@@
   systems respectively.
-
+  \clearpage
   \begin{figure}[!htb]
@@
   \caption{The water content in the tail and pore region is not affected
-  by cross-linking}\label{fig:solvation_equilibration}
+  by cross-linking}\label{fig:xlinked_solvation_equilibration}
   \end{figure}
@@
   \clearpage
-
   \section{Solute Interaction}\label{section:solute_interaction}
@@
 %  \end{figure}
-  \clearpage
+
   \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}
@@
   We chose to report the MSD of our solutes after a 400 ns time lag. This choice does
-  not have a significant influence on the ranking of the solute MSDs. Although there
-  is minor re-ranking among solutes with similar MSDs, it does not affect any of 
-  the conclusions drawn in the main text.
+  not have a significant influence on the ranking of the solute MSDs (see 
+  Figure~\ref{fig:lag_sensitivity}). Although there is minor re-ranking among solutes
+  with similar MSDs, it does not affect any of the conclusions drawn in the main text.
 
@@
   \clearpage
+
   \section{Pore Region Definition}\label{section:pore-region}
@@
 
-  \begin{figure}
+  \begin{figure}[H]
   \centering

### 2019-06-25 Ben_Manuscripts/transport/response_to_reviewers.tex
Made sure response to reviewers matches main text

@@
 
-    New text: ``This behavior is likely due to the much more crowded pore environment
-    in the 5 wt\% versus the 10 wt\% water system. Monomer head groups are
-    concentrated about 2\AA~closer to the pore centers in the 5 wt\% versus the 10 
-    wt\% water system (see Figure~\ref{M-fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water 
+    New text: ``This behavior is likely due to the
+    much more crowded pore environment in the 5 wt\% versus the 10 wt\% water system. 
+    Monomer head groups are concentrated about 2~\AA~closer to the pore centers in the
+    5 wt\% versus the 10 wt\% water system (see Figure~\ref{M-fig:component_densities})
     which leaves less space for water molecules and restricts their movement among the 
@@
     molecules in the pores of the 5 wt\% water system associate with a sodium ion each
-    frame compared to 44\% in the 10 wt\% water system.
-	There are about half as many water molecules in the 5 wt\% water system which allows a 
-	larger fraction of them to associate with sodium ions. The lifetime of associations
-	between sodium ions and water is 7.5 ns and 3.0 ns in 5 and 10 wt\% water systems respectively.``
+    frame compared to 44\% in the 10 wt\% water system.There are about half as many water
+    molecules in the 5 wt\% water system which allows a larger fraction of them to 
+    associate with sodium ions. The lifetime of associations between sodium ions and 
+    water is 7.5 ns and 3.0 ns in 5 and 10 wt\% water systems respectively.``
 
@@
     and solutes partition into the tails, an area previously assumed to be devoid of solutes,
-    which offers another route towards selectivity.
-    The interactions we observed, along with those that may arise in other self-assembled
-    nanoporous membranes, have the potential to produce an immense diversity of transport
-    behavior, suggesting that a previously unexplored range of chemical selectivities may
-    be possible. Atomistic molecular modeling is likely to be highly useful in uncovering 
-    important mechanisms that will inspire and accelerate novel design by experimentalists.''
+    which offers another route towards selectivity. The interactions we observed, along 
+    with those that may arise in other self-assembled nanoporous membranes, have the 
+    potential to produce an immense diversity of transport behavior, suggesting that a 
+    previously unexplored range of chemical selectivities may be possible. Atomistic 
+    molecular modeling is likely to be highly useful in uncovering important mechanisms
+    that will inspire and accelerate novel design by experimentalists.''
 
@@
 
-	New text: ``We simulated water molecules using the TIP3P water model because it 
-	because it is the water model that GAFF and other AMBER family parameters were optmized with.''
+	New text: ``We simulated water molecules using the TIP3P water model because it is
+	the water model that GAFF and other AMBER family parameters have been optimized
+    with.''
 %    computationally efficient and reasonably reproduces water's physical properties
@@
 
-    %BJC2: incorporated point about pore size
     New text: ``The equilibrated unit cells have different geometries depending on water
@@
     regions. Rather, there is a gradual transition from the hydrophilic to hydrophobic region.''
-    %MRS2: should also talk about where this is discussed in THIS paper.  We want to make sure people are 
-    % visualizing what we are imagining when reading this paper.
 

### 2019-06-25 Ben_Manuscripts/transport/Final_Draft.tex
Made sure response to reviewers matches main text

@@
 
-\title{Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Chemically Selective Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 \author{Benjamin J. Coscia}
@@
   promising candidates for selective separations.
-  %that 
-  %constitute cross-linked inverted hexagonal (H\textsubscript{II})
-  %phase lyotropic liquid crystal (LLC) membranes make them promising
-  %candidates for selective separation membranes. 
-  %MRS3: I do worry that the above makes it look like we are not acknowledging
-  %the formulation problems.  Maybe something like: ''models of how chemically
-  %selective separation membranes could can function''?  So the focus is more
-  %on the science that these membranes could reveal, rather than saying they
-  %are good membranes now?  Then we talk about new membranes at the end of the
-  %introduction. Thoughts? I didn't go ahead and make  the change since it
-  %needs a bit more thought.  I'm open to other ways to reformulate.  Some of
-  %this thinking will percolate into the rest of the introduction as well.
   In this work, we observe transport of water, sodium ions and 20 small polar
@@
   size, limiting their selectivity.~\cite{werber_materials_2016}.
-%  Therefore, multiple membrane passes may be necessary in order to achieve 
-%  high selectivity.
-
-%  A membrane with the
-%  selectivity of an RO membrane and the permeability of an NF membrane would
-%  offer a significant improvement to current commercial membrane technology.
-%  Nanostructured membranes offer the potential for molecular-level design 
-%  which could overcome the limitations faced by conventional membrane 
-%  technologies. One can create dense arrays of well-defined uniform-sized
-%  \begin{itemize}
-%    \item Mitigation of stochastic aspects of membrane synthesis
-%    \item Well-defined and uniform pores increase selectivity
-%    \item Solute-specific separations.
-%  \end{itemize}
-
-% re-outline from here.
-
-%  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
-%  membranes are nanostructured membranes that may be able to achieve the
-%  selectivity of RO membranes while maintaining the high permeability
-%  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
-%  phase is formed when LLC monomers self-assemble into hexagonally packed
-%  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
-%  cross-linking of the hexagonal mesophases yields a mechanically strong
-%  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
-%  enforce a strict molecular-size cut-off while the hexagonal geometry is 
-%  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
-%  because the LLC monomers are salts, Donnan exclusion plays a role in 
-%  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
-
-  %BJC4: generalized to amphiphilic self-assembled structures.
+
   Under the right conditions, amphiphilic molecules can self-assemble into
@@
 
-  %BJC4: bring it back to LLCs but don't make it seem like HII is the best
   Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
@@
 
-  % Highlight that QI has the best chance.
   Although Q\textsubscript{I} membranes have shown promising results, it
@@
   of governing molecular interactions.~\cite{dischinger_effect_2017}
-
-%  Zhou et al. demonstrated complete rejection
-%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
-%  membranes.~\cite{zhou_supported_2005}
-
-%  In addition to geometric factors which make H\textsubscript{II} membranes
-%  ideal for selective separations, they have the potential to further disrupt
-%  conventional membrane separation techniques by being selective based not
-%  only on solute size and charge, but on chemical functionality as well. 
-%  The functional LLC monomer head groups that occupy the pore region of the
-%  membrane can interact with solutes. Dischinger et al.~studied the 
-%  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
-%  similar pore topology to the H\textsubscript{II} phase, but a more 
-%  tortuous geometry, and observed a range of selectivities dependent on the
-%  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
-%  design of LLC monomers have the potential to help us tailor membranes for 
-%  solute-specific separations.
-
-%  While H\textsubscript{II} membranes have been synthesized and characterized
-%  in a lab setting, there is a limit to the level of detail that can be obtained 
-%  from experiment. These membranes have been primarily characterized with 
-%  size-exclusion experiments which can give an estimate of pore size as well as
-%  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
-%  However, size exclusion does not appear to be sufficient to fully describe LLC
-%  membranes. Dischinger et al. studied a similar membrane and found that they do
-%  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
-%  between various solute physicochemical properties and observed solute rejection. 
-%  Although there was some agreement with their empirical model, it does not
-%  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
-%============= 
-%  The separation performance of these membranes has been 
-%  primarily characterized with size-exclusion experiments which emphasizes 
-%  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
-%  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
-%  %separation BY size exclusion; maybe rephrase?
-%  %BJC4: Hmm, by characterization, I mean testing their ability to separate, so I'm 
-%  While size-exclusion is a useful separation, it 
-%  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
-%  important to take advantage of material properties other than pore size. 
-%  Unfortunately, this is a more complicated design problem. Experimental transport
-%  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
-%  unclear trends due to interactions between solutes and pore moieties. Although
-%  the authors identified some correlation between select physicochemical properties
-%  and solute transport trends, their empirical model does not offer a sufficient 
-%  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
-  %MRS4: expand the above.  What was discovered, and why was it unfortunate to the thesis?  
-  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
 
@@
 
-  %BJC4: also edited here to help with the flow.
   In this work, we present studies of the transport mechanisms exhibited by 20
@@
 
-  %BJC4: not sure if I should add a thesis to this paragraph, reattach above, or just
-  % leave as is since it's informational.
   Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of the
@@
   and are used in many plots. 
-%  Blue corresponds to simple alcohols, red to 
-%  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
-%  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.
   }\label{table:abbreviations}
   \end{table}
-
-  %MRS2: generally, use present tense for what is being done in the paper, not future tense; 
-  %the paper is completely written, later sections are not being written in the future. 
-  %MRS2: descriptions of experiments can be in the past.   
-  %MRS2: look over this section at the end of the intro again for clarity - some paragraphs are too short (ideas introduced and brushed past quickly) sometimes without strong theses.
-  %BJC3: I think these make more sense now.
 
@@
 
-%  We then present our efforts to understand how water partitions within the pores.  
   We then use the transport rates of water in and out of the pores in order to
@@
   our most viable system, water moves fastest within the pores suggesting that 
-  the 
-  %MR3: added to be more specific - we do look at it getting into the head groups a little.
-  area in and around the central
-  pores should be the focus of our mechanistic studies.
-
-  %MRS2: ``this information'' is ambiguous. Which information? Also, I'm not sure the paragraph above is enough to 
-  %demonstrate why we can/should neglect the tails.
-%  We use this information in order to justify our restriction
-%  of solute transport studies to just the pore region.
-
-%  We then study the gradient in composition of solutes and 
-%  water and any resultant influence it might have on mechanistic properties.
+  the area in and around the central pores should be the focus of our mechanistic studies.
 
@@
   We simulated water molecules using the TIP3P water model because it is the
-  water model that GAFF and other AMBER family parameters have been optmized
-  with.~\cite{florova_explicit_2010} %~\cite{mahoney_five-site_2000}
+  water model that GAFF and other AMBER family parameters have been optimized
+  with.~\cite{florova_explicit_2010}
 
@@
 
-%  We observed that some water partitions into the distal tail region of our system and therefore
-%  built our initial configurations with water in both regions, close to the expected
-%  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
-%  Information). We define the distal tail region to be ca. 1.5 nm from the pore
-%  center based on the minimum in the radial distribution function of water
-%  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
-%  may or may not be experimentally consistent but it is necessary for our results to be 
-%  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
-%  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
-%  until the appropriate amount of water fit in the pores after running the GROMACS command
-%  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
-%  in random locations with a short energy minimization between each insertion. When 
-%  studying transport of water in the pores, we limited the calculations to water molecules
-%  that spent greater than 95\% of their time outside of the distal tail region. We 
-%  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
-
-%  We fully equilibrated an initial solvated configuration before adding solutes. First, we 
-%  equilibrated the initial configuration using the `wet' equilibration procedure 
-%  described in our previous work. Then we cross-linked the equilibrated solvated 
-%  configuration using the cross-linking procedure also described in our previous 
-%  work.~\cite{coscia_understanding_2019}
-
   The equilibrated unit cells have different geometries depending on water
@@
   the hydrophilic to hydrophobic region. 
-
-%  The approximate size of the pore region and the 
-%    boundaries we defined are addressed later in the methods and throughout the results and 
-%    discussion section.
+  %We observe the same architecture in the systems
+  %studied in this paper (see Section~\ref{section:membrane_components}).
 
@@
   motion respectively.
-    % MRS1: time vs. ensemble MSD better in follow-up paper.
-    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
-    % fully understand the theory since I talk about subdiffusion in terms of 
-    % alpha which is always calculated based on ensemble MSD unless we know for sure that
-    % the system is ergodic (which it isn't the case for CTRW)
+
   In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
@@
 
-  % BJC: haven't talked about hopping mechanism at this point, but need to justify why
-  % I used total MSD rather than fitting some function to it
   We fixed the length of each simulated trajectory so that we could compare the total
@@
   statistical precision. Therefore, for the purpose of comparison, we calculated its
-  %BJC3: linear within statistical precision --> appears linear? I didn't do any rigorous tests for linearity
   diffusion constant by fitting a line to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
@@
 
-  %MRS4: a bit strange to say you are using Stokes-einstein, but only analyzing MSD's (when MSD's don't appear in that equation)? It could be clarified a bit more.
-%  However, this assumes linear behavior
-%  of the MSD, which we will show is not that case. Our main usage of the 
-%  Stokes-Einstein relationship is to show that solutes in our system do not 
-%  behave as it predicts.
-  % Possible comps question: Stokes law restricted to Re < 0.1, but we have no flow so Re ~ 0.
-
   Since we will be using Equation~\ref{eqn:msd-stokes-einstein} for primarily qualitative observations, 
@@
   using a constant scaling factor. \cite{lee_molecular_2008,he_novel_2003,li_critical_2009}.
-  % BJC: could just calculate Rg instead of end-to-end
   Assuming that our end-to-end distance reasonably approximates R\textsubscript{g} 
@@
 
-  %BJC: another option is to fit to water which IS Brownian in the 10 wt% system.
   We fit Equation~\ref{eqn:msd-stokes-einstein} so that it passed through the
@@
   same value as the corrected curve for large radii.
-  % BJC: Set really high intersection value. Converges quickly (i.e. critical radius
-  % (the radius where curves intersect) of 2.5 nm looks almost the same as critical
-  % radius of 100 nm. I don't think this necessarily needs to be proved anywhere
-
-%  at the critical particle radius 
-%  where the uncorrected Stokes-Einstein begins to break down. An exact critical
-%  radius is not well-defined, but based on the observations of others, we will
-%  approximate that radius as 2.5 nm\cite{li_critical_2009,polson_some_1950}. The 
-%  sensitivity of the uncorrected curve to this intersection radius is shown to 
-%  be small and is graphically illustrated in Section-TBD of the Supporting Information.
-
-%  It is well-known that equation~\ref{eqn:stokes-einstein} breaks down Gierer and Wirtz introduced a microfriction
-%  correction factor in order to address this issue. 
-%  They proposed that 
-%  \begin{equation}
-%  D = \dfrac{k_bT}{6\pi\eta fr}
-%  \end{equation}
-%  where
 
@@
   cumulative distribution function and scaled them to a per--nanosecond basis.
-
-%  We used the normal 
-%  approximation in order to estimate the 95 \% confidence interval
-%  of these estimates:
-%  \begin{equation}
-%  95\%~CI = 1.96 \sqrt{\dfrac{\lambda}{n}}
-%  \end{equation}
-%  where $\lambda$ is the average frequency of hops and n is the total
-%  observation time accumulated for all solutes.
 
@@
   of these events into a distribution of association lifetimes.
-  %BJC: could justify why I didn't use autocorrelation functions
-
-  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
-  % me maybe half a day to implement and generate results. Not sure if necessary though since
-  % I'm just going to say that I don't know what distribution it is and we are going to
-  % use a percentile.
-  % MRS4: maybe while we are waiting for review.
+
   Hydrogen bond lifetimes appear to be distributed according to a power law or an
@@
 
-%  of each individual
-%  head group. For each head group, we obtained an RDF averaged over the
-%  entire simulation trajectory. We randomly chose head group RDFs with replacement
-%  and averaged them for each bootstrap trial. This approach assumes that
-%  head group positions are uncorrelated.
-
   \section{Results and Discussion}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{component_density_dry.pdf}  % running this out on bridges to make smoother
-  %BJC: simulation is extended to smooth out these curves
-  %BJC3: update: got slightly smoother
+  \includegraphics[width=\textwidth]{component_density_dry.pdf}
   \caption{Dry System}\label{fig:component_density_dry}
@@
   \end{subfigure}
-  %MRS2: interesting that the head group max is near the transition point where water/tail groups 
   \caption{The radial densities of various monomer components paint a 
@@
 
-  %MRS2: probably would be better to consolidate the information about water in the tails in one place.  Could be here?
-  %MRS2: fundamentally, needs to be explicit justification of the choice to look at transport in the pores alone.
-
   There is an appreciable amount of water that partitions into the distal tail
@@
   monomer tail which can further stabilize water molecules.
-
-  %See Figure~\ref{S-fig:total_density} of the Supporting 
-  %Information for a graphical illustration of this point.
 
@@
 
-  % Plots generated with msd_curves.py in figures folder
-  % BJC: I show up to 400 ns time lag. Any reason to show full 1000 ns?
   \begin{figure}[!htb]
@@
   sodium ions considerably compared to in bulk water.
-  %MRS2: is one sodium per carboxylate group correct?
-  %BJC3: yes, if sodium within cutoff of both oxygens, it is only counted once.
-  % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
-  % since the averages were divided by 800 instead of 400
 
@@
 
-  % Changing does not change conclusion here.
   In the 5 wt\% water system, water molecules that spend the majority of their 
@@
   Monomer head groups are concentrated about 2~\AA~closer to the pore centers in the
-  5 wt\% versus the 10 wt\% water system (see Figure~\ref{fig:component_densities})  %BJC: this is the RDF figure of head groups, tails, sodium, water 
+  5 wt\% versus the 10 wt\% water system (see Figure~\ref{fig:component_densities})
   which leaves less space for water molecules and restricts their movement among the 
@@
 
-%  The reason for this anomaly is twofold. 
-%  First, monomer head groups are concentrated about 0.2 nm closer to the pore centers
-%  in the 5 wt\% versus the 10 wt\% water system (see Figure~\ref{fig:component_densities})
-%  which results in more frequent collisions between water molecules and relatively immobile 
-%  monomer head groups. Second, the diffusion of water molecules is slowed via hydrogen
-%  bonds with other water molecules and association with sodium ions. Notably, there is a 
-%  negligible number of hydrogen bonds between water molecules and monomer head groups. 
-%  The 95th percentile lifetime of hydrogen bonds between water molecules located near the
-%  pore center is 2.1 ns in the 5 wt\% system compared to 0.5 ns in the 10 wt\% system. 
-%  However, since we only saved simulation output every 0.5 ns, it is likely that the 
-%  true hydrogen bond lifetimes in the 10 wt\% system are smaller than this value. 
-%  With regard to sodium ions, more frequent and longer periods of association
-%  with water molecules helps to drive down water's MSD. An average of 65\% of water 
-%  molecules in the pores of the 5 wt\% water system associate with a sodium ion each
-%  frame compared to 44\% in the 10 wt\% water system. There are about half as many water
-%  molecules in the 5 wt\% water system which allows a larger fraction of them to associate
-%  with sodium ions. The lifetime of associations between sodium ions and water is 7.5 ns
-%  and 3.0 ns in 5 and 10 wt\% water systems respectively.
-
-%  Water molecules 
-%  are less likely to hydrogen bond with each other while in the distal tail region 
-%  since they are interspersed between chains, while those in the pores stay in close
-%  proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
-%  hydrogen bonding between water molecules near the pore center versus those in 
-%  the distal tail region.
-
-%  is anomaly is likely a 
-%  consequence of lower density in the distal tails relative to the pores,
-%  leading to faster diffusion in the tails,
-%  as well as slowed diffusion of water molecules in the pores via hydrogen bonds
-%  with other water molecules and association with sodium ions. Water molecules 
-%  are less likely to hydrogen bond with each other while in the distal tail 
-%  region since they are interspersed between chains, while those in 
-%  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
-%  hydrogen bonding between water molecules near the pore center versus those in 
-%  the distal tail region. Additionally, an average of 65\% of water molecules in
-%  the pores of the 5 wt\% water system are associated with a sodium ion each frame
-%  compared to 44 \% in the 10 wt\% water system. There is a negligible amount of
-%  hydrogen bonds between water molecules and monomer head groups.
-
   Because the MSD of water in the pores of the 10 wt\% system is significantly
@@
   wt\% system.
-
-%  45 \% of water molecules associated with sodium in 5 wt\% system
-%  
-%  While a similar observation holds for the 10 wt\% system,
-%  its high water content facilitates a less crowded environment where diffusion
-%  of water molecules dominates.  
-%  %MRS4: math seems a little inconsistent.  Does the tail water move the same rate in 5 and 10%? Seems like it should.
-%  %MRS4: but above would tend to indicate that it moves 51/8 = 6.4 times faster in the tails in 10%? 
-%  %MRS4: think about reading over/describing the tail water here
-%  %MRS4: would probably be useful to the reader to specify that we are neglecting transport in the tails here.
-%
-%  Hydrogen bonds to charged things. Dipole-point charge stronger than dipole-dipole
-%  Quantify water 
-%
-%  10 wt will be the only practical membrane.
-%
-%  Set up simulations with high percent methanol
 
@@
   \end{subfigure}
-  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
-  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
   \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
@@
 
-%  Solutes partition out of the pore into the head group region and beyond
-%  which may lead to a radially dependent transport mechanism. It is clear 
-%  from Figure~\ref{fig:example_ztraces} that the longest periods of 
-%  entrapment usually occur when solutes are far from the pore center.
-
-  % When hops occur, and where there is the most $z$-positional
-  % noise, solutes are generally close to the pore center
-
   \begin{figure}
@@
 
-  %In addition to solute trapping in dense monomer regions, 
   We observe a second trapping mechanism caused by preferential hydrogen 
@@
   continue with our ethanol example, we observe that 64\% of ethanol
-  molecules donate hydrogen bonds  % 15.7/24 donated, 0.6/24 accept -- BJC: double check these numbers
+  molecules donate hydrogen bonds
   and 3\% of ethanol molecules accept hydrogen bonds each frame. On average, 40\%
-  of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
+  of hydrogen bonds donated by ethanol go to carboxylate 
   head groups, 25\% go to the ether linkages connecting the monomer tails to the 
-  head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molecules in pores 
+  head groups and the remaining 35\% to water. There are about 46\% less 
   carboxylate oxygen atoms in the pore than there are water molecules yet more
@@
   hydrogen bonds from solutes.
-  % MRS1: this should lead to reduced ability to solvate positive things, but 
-  % shouldn't reduce H-bonding that much?
-  % BJC1: I think that it takes away acceptor oxygen atoms since they are occupied
-  % by sodium. The hydrogen atoms of water could still hbond but I'm just talking
-  % about ethanol donating to water's oxygen, for which opportunities should be suppressed.
 
@@
 
-%  The dwell times are power law 
-%  distributed, which means that while many of these interactions are fleeting,
-%  there is still a chance for very long periods of association to occur. For 
-%  example, the longest period of coordination between acetone and sodium was
-%  110 ns.
-%  There are many cases, particularly when an electronegative atom is left unprotected,
-%  in which polar groups bind to sodium ions for at least a short period of time.
-
-  % need to think a little more about this. Numbers get skewed by different numbers
-  % of oxygen atoms per solute. For example, the carbonyl group of acetic acid
-  % associates with sodium a lot, but the OH doesn't really. (28 % C=O versus 3 % COH)
   \begin{figure}[!htb]
   \centering
-  % BJC: maybe I should normalize these to number of oxygen atoms?
   \begin{subfigure}{0.45\textwidth}
@@
   molecules in the discussion that follows.
-  % We will make reference to the figures in this section
 
@@
   groups.
-  % BJC: could say something like the following
-  % The hop lengths and frequencies are not exceedingly small for any of the
-  % simple alcohols, but their high density near the head groups suggests that
-  % the hops may be anti-correlated, yielding low MSDs especially as the solutes
-  % get larger.
-
-%  Methanol moves fast because it is the smallest solute studied in this work and
-%  it has a high radial density near the pore center where the largest hops occur.  % actually spends a small amount of time there relative to other solutes.
-%  The radial density as a function of distance from the pore center for each
-%  alcohol is plotted in Figure~\ref{fig:simple_alcohol_rdf}. On average, the 
-%  density of methanol in the pore center is only slightly less than the density
-%  near the head groups. All other alcohol molecules are most concentrated near 
-%  the head groups.
 
@@
   \end{subfigure}
-  %MRS4: suggest putting something at the beginning of the caption indicating which chemical group it is.
-  %BJC3: added to first sentence of caption
   \caption{(a) The MSD of the simple alcohols decrease as a function of the
@@
   molecule in place and allow the previously broken bond to reform.
-%  Hydrogen bonds act as a kind of 
-%  molecular glue which holds solutes in place, especially when there are many.
   Proximity to the pore center partially compensates for this effect in
@@
   RDF about 0.2 nm from the pore center. 
-%  However, acetic acid spends 
-%  significantly more time in the pore center and therefore encounters more sodium ions. 
-  %When an acetone molecule coordinates with a sodium ion, its polarity is
-  %largely neutralized and it retreats towards the head group region where it can easily
-  %get trapped. 
   Acetic acid and the amides have other, unoccupied, hydrophilic groups while
@@
   \begin{subfigure}{0.45\linewidth}
-  %BJC: should I plot ethylene glycol, glycerol and acetone MSDs here as well?
   \includegraphics[width=\textwidth]{msd_radius_sulfur_10wt.pdf}
@@
   immobile outside of the pore, but moves quickly inside.
-%  Mercaptoethanol also hydrogen bonds with head groups about 16\% less 
-%  %BJC: 16\% less meaning 64.3 % - 48.3 %. Not sure if it is better to say (64.3 - 48.3 / 64.3) = 25 %
-%  frequently. Consequently, shorter hydrogen 
-%  bond lifetimes within the pore region may yield some high MSD 
-%  trajectories.
-
-%, which is less than expected if equal amounts of both 
-%  solutes occupied the pore region. 
-% (20.2 - 12.857) / 20.2 = .364
-% (12.857 + 6.8215 + 0.803) / (20.2 + 11.969 + 1.935) = 0.6
-%  There are nearly 40\% more mercaptoethanol 
-%  molecules than ethylene glycol molecules beyond 0.8 nm  % ratios.py in figures folder
-%  from the pore center. 
-%  The average length
-%  of a hop performed by a mercaptoethanol molecule within 0.8 nm of the pore 
-%  center is 1.43 nm compared to 1.20 for ethylene glycol. % hop_location.py. Even larger difference if cut-off lower
 
@@
   spends 27\% less time in the pore region than glycerol. 
-  %BJC: again, not sure if this should be 27\% because DMP spends 49% of time in pore and GLY spends 76% of time in pore or if it should be (76 - 49) / 76 = 36 %
-%  The density of glycerol is always higher up to 0.7 nm from the pore center where the 
-%  population of 2,3-dimercapto-1-propanol then becomes more dense into the tail region.
   Glycerol participates in about 2.5 times as many hydrogen
-  bonds as 2,3-dimercapto-1-propanol (including all possible hydrogen bonding groups).  % BJC: might be confusing. Maybe refer to figure 6 instead.
-  % BJC: sums are (donate to monomer + receive from water + donate to water).
-  % BJC: (31.91 + 17.224 + 3.231) / (13.1 + 7.737 + 0.8965) ~= 2.45.
-  % (2.788 + 2.0975 + 0)/ (13.1 + 7.737 + 0.8965) = 0.22
+  bonds as 2,3-dimercapto-1-propanol (including all possible hydrogen bonding groups). 
   Only 22\% of the hydrogen bond interactions of 2,3-dimercapto-1-propanol
@@
   (see Figure~\ref{fig:msds}). DMSO spends 17\% more time in the pore than acetone. 
-%  The density of DMSO is higher than acetone in the pore region, except for
-%  the peak exhibited by acetone near 0.2 nm, which is due to sodium ion association.
   On average, 35\% of DMSO molecules are coordinated to a sodium ion each
@@
 
-%  The solutes in this set do not make frequent hops while in the pore region. 
-%  % Time bound to sodium ion
-%  % Number of hops in pore region
-%  \begin{itemize}
-%%	\item Observations of single THF trajectories have revealed that it becomes 
-%%	nearly immobilized while associated with sodium ions 
-%%	(See Figure~\ref{fig:thf_sodium_coordination}).
-%	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
-%	higher than THF near the head groups. The planar shape of DMF causes it to 
-%	become stuck between head groups. Excursions into the pore region do not
-%	necessarily result in large hops.
-%  \end{itemize}
-
   Carbonyl groups continue to show high degrees of association with
@@
   \begin{subfigure}{0.325\textwidth}
-  %BJC: trying out pore region cut-off here instead of head groups.
   \includegraphics[width=\textwidth]{nondonors_rdf.pdf}
@@
   which may eliminate their interaction with most solutes.
-
-%  The findings here are likely too complex to point towards a clear design of an 
-%  optimal LLC membrane for a particular separation. This work does demonstrate
-%  that there is a large range of solute-membrane interactions resulting from the
-%  chemically complex and inhomogeneous LLC membrane structure. The varying 
-%  chemical functionality of the solutes themselves gives rise to an immense diversity of
-%  transport behavior. This behavior suggests that a large range of chemical 
-%  selectivities may be possible in self-assembled nanoporous membranes. Atomistic
-%  modeling gives us the opportunity to observe these interactions at the molecular
-%  scale, at least approximately, so that we can think more critically about 
-%  nanostructured membrane design.
-
-%  Our work demonstrates that one cannot rely solely on chemical intuition while 
-%  designing LLC membranes for particular separations. The complex interplay between the
-%  inhomogeneous membrane structure, solute size and solute functionality leads to a variety of
-%  solute-membrane interactions, of which many are quite subtle. For example, association
-%  between polar groups and ions is seldom mentioned in the literature, but we could not give a
-%  complete mechanistic explanation of observed transport behavior without its consideration. 
-%  The interactions we observed, along with those that may arise in alternative self-assembled
-%  nanoporous membranes, can lead to an immense diversity of transport behavior which suggests
-%  that a large range of chemical selectivities may be possible. Atomistic molecular modeling
-%  may be the best hope of uncovering the dominant mechanisms that will inspire and accelerate
-%  novel design by experimentalists.
 

### 2019-06-25 Ben_Manuscripts/transport/Final_Draft.tex
Added one more citation for TIP3P justification

@@
   water model that GAFF and other AMBER family parameters have been optimized
-  with.~\cite{florova_explicit_2010}
+  with.~\cite{florova_explicit_2010,ponder_force_2003}
 

### 2019-06-25 Ben_Manuscripts/transport/response_to_reviewers.tex
fixed a coupel of typos.

@@
     molecules in the pores of the 5 wt\% water system associate with a sodium ion each
-    frame compared to 44\% in the 10 wt\% water system.There are about half as many water
+    frame compared to 44\% in the 10 wt\% water system. There are about half as many water
     molecules in the 5 wt\% water system which allows a larger fraction of them to 
@@
 
-    %MRS: TIP-4P is pretty close in efficiency, and TIP3P is only mediocre in bulk water properties  I would probably say that TIP3P was used because it is the water model that GAFF and other AMBER family parameters were optmized with.
+    %MRS: TIP-4P is pretty close in efficiency, and TIP3P is only mediocre in bulk water properties  I would probably say that TIP3P was used because it is the water model that GAFF and other AMBER family parameters were optimized with.
 TIP3P also diffuses faster than experimental water, which is both a negative (can't compare absolute diffusion) and positive (things happen faster).
@@
 
+    %MRS3: fix accents below in LaTeX.
     Florová, Petra, Petr Sklenovský, Pavel Banáš, and Michal Otyepka. “Explicit Water 
@@
     Conformational Behavior and Flexibility of Folded Peptides Remain Intact.” Journal 
-    of Chemical Theory and Computation 6, no. 11 (November 9, 2010): 3569–79. https://doi.org/10.1021/ct1003687.
+    of Chemical Theory and Computation 6, no. 11 (2010): 3569--79. https://doi.org/10.1021/ct1003687.
 
@@
 
-    Old text: `` We observed that some water partitions into the distal tail region of our system and therefore
+    Old text: ``We observed that some water partitions into the distal tail region of our system and therefore
 	built our initial configurations with water in both regions, close to the expected

### 2019-06-28 Ben_Manuscripts/stochastic_transport/Outline.tex
Stochastic transport manuscript initialization

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

%BJC: potential titles (uncommented is current favorite)
%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

\begin{document}

  \graphicspath{{./figures/}}
  \maketitle

  \section{Introduction}

  We need highly selective membranes in order to perform efficient separations.

  Amphiphilic molecules are capable of self-assembling into ordered nanostructures.

  Lytropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
  into mechanically strong membranes.
  \begin{itemize}
  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
	sized pores and have the potential to disrupt conventional membrane separation
	techniques by being selective based not only on size and charge, but on chemical
	functionality as well.
	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
	pores.
  \end{itemize}

  We can only learn so much from experiment. MD can give us mechanistic insights with
  atomistic resolution so that we can intelligently design new membranes for 
  solute-specific separations.

  In our previous work, we studied the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane.

  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to predict macroscopic transport properties traditionally used to characterize
  membranes in the lab.

  % review of techniques for predicting long time scale behavior

  In this work, we have determined the transport mechanisms and macroscopic
  transport properties exhibited by a number of polar solutes with varying size,
  chemical functionality and hydrophilic character.
  \begin{itemize}
	\item Many of the separations we are interested in involve polar organic 
	compounds.
  \end{itemize}

  We have compared our calculated diffusion coefficients with experimental
  measurements made using DOSY NMR.

  \section{Methods}

  \subsection{Molecular Dynamics Simulations}

  \subsubsection*{System Setup}

  There is a broad range of water concentrations which will form a stable 
  H\textsubscript{II} phase with Na-GA3C11. 
  \begin{itemize}
	\item In the literature this system is typically synthesized with close
	to 10 wt \% water
    \item However, Resel et al. noted that the system is likely fully 
	hydrated with less than 7 wt \% water.
	\item We decided to test two different levels of water content: 5 and 10 wt \%
  \end{itemize}

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

%  We equilibrated the initial configuration using the `wet' equilibration procedure
%  described in our previous work (reference to structure paper).
  %BJC: not sure I need to go into any details describing that procedure
%  \begin{itemize}
%	\item Series of NVT simulations with force constants on carbon atoms of aromatic
%	ring in head group
%	\item Force constants reduced according to the sequence: 1000000, 3162,
%	56, 8, 3, 2, 1, 0 kJ mol$^{-1}$ nm$^{-2}$ 
%  \end{itemize}

%  We cross-linked the equilibrated solvated configuration using the cross-linking procedure
%  described in our previous work.

  We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimzation.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using long simulations, on the order of
	1 microsecond
	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
  \end{itemize}

  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}

  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
  behavior, a type of anomalous diffusion. 
  \begin{itemize}
  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
  	does not grow linearly with time, rather it is of the form:
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
	motion respectively.
  \end{itemize}

  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
  of the simulated trajectories.
  \begin{itemize}
	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
	position~\cite{meroz_toolbox_2015} and can be written as
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
%	\item The average MSD calculated in this way recovers the form of
%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
	\item The time-averaged MSD measures the displacement between all possible time lags
	and can be written as
	\begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
%	\item The time-averaged MSD becomes linear in our simulations,
%	therefore we can fit a line to its slope in order to estimate the macroscopic
%	diffusivity of the particle.
	%BJC: this needs more justification. Not many people have done it
	%BJC: could also not report them as diffusivities. Comparison of total MSD
	% should give same information
	% Linear region probably exists because dwell times on the order of large lag times
	% become negligible
  \end{itemize}

  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
  continuous time random walks (CTRW), fractional Brownian motion (FBM) and
  random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  \begin{itemize}
    \item FBM is common in crowded, viscoelastic environments where each step comes 
    from a Gaussian distribution but is anti-correlated to its previous 
    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
    \item A CTRW is characterized by a distribution of hop lengths and 
    dwell times, where each each step is characterized by independent random draws from 
    each distribution.\cite{montroll_random_1965,morrin_three_2018}
    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
    \item The processes described above can happen alone or in combination.  	
  \end{itemize}

  \noindent We believe that solutes in the system studied here exhibit subordinated 
  fractional Brownian motion (sFBM) where the parent process is FBM and the 
  leading process is a CTRW. 
  \begin{itemize}
  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
  	\item We also observe non-stationary $z$-coordinate traces of each solute's
  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
  	\item For a pure CTRW, the time-averaged MSD should be linear.
  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
  	information), which suggests that there is another underlying subdiffusive mechanism.
  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
  	\item Given the viscoelastic nature of the monomers in our system, we believe
  	the hop lengths can be modeled with FBM. 
 	\item For subordinated FBM, it can be shown that
  	\begin{equation}
  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
  	\end{equation}
  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
  \end{itemize}

  \noindent We can characterize a CTRW process using the parameters which describe its
  dwell time and hop length distribution.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct empirical distributions.
	\item For solutes in our system, the distribution of hop lengths is
	well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
	metzler_anomalous_2014,neusius_subdiffusion_2009}
	\item We are most interested in the standard deviation, $\sigma$, of the 
	hop length distribution.
	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	empirical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powerlaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
  \end{itemize}

  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
  $H = \beta/2$.
  \begin{itemize}
  	\item Brownian motion is recovered for $H = 0.5$
	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
    \begin{equation}
	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
	\label{eqn:autocovariance}
	\end{equation}
	where $k$ is the number of increments between hops.
	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
	to the empirically measured autocovariance function.
	\item We used statistical bootstrapping to generate a distribution of $H$ 
	values. %BJC: can provide more detail in supporting or just reference python script
  \end{itemize}

%  We generated distributions of parameters for the dwell time and hop length
%  distributions using statistical bootstrapping.
%  \begin{itemize}
%	\item For each type of distribution, we randomly selected $n$ data points from the empirical
%	distribution with replacement.
%	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
%  \end{itemize}

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
  \begin{itemize}
	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
	distributions.
	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
	the last data point so that the total time exactly equaled 1 $\mu$s. 
    \item Valid comparisons are only possible between fixed length sFBM simulations. The
    power law dwell time behavior gives rise to the aging phenomenon, embodied by
    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
% Following probably better suited for supporting information, if included at all
%	\item We randomly sample Gaussian hop lengths using the
%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%	\item We randomly sampled dwell times from a discrete power law
%	distribution based on the recommendations of Clauset et
%	al.~\cite{clauset_power-law_2009}: 
%	\begin{equation}
%	x = \lfloor
%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%	\label{eqn:discrete_powerlaw_draws}
%	\end{equation}
%	where $r$ is randomly drawn from a uniform distribution which we simulated
%	with \texttt{numpy.random.uniform}.
%	\item We found that thermal noise does not significantly influence the MSD and
%	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

%BJC: probably don't need to explain this in great detail
%  \noindent We fixed the length of each simulated trajectory so that we could compare the total
%  MSD between different solutes without the influence of the ageing phenomenon.
%  \begin{itemize}
%	\item Ageing is defined by the tendency of the average MSD to decrease
%	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
%	\item The maximum measured dwell time can be no longer than the total length
%	of a simulated trajectory. 
%	\item As measurement time or trajectory length is increased, longer dwell times
%	are incorporated into the calculation, lowering the average MSD. (See supporting
%	info for demonstration)
%	\item We can achieve consistent total MSDs with low uncertainty for
%	simulated trajectories created with a given set of parameters if we fix the
%	trajectory length (as opposed to total number of steps).  
%  \end{itemize}

  \subsubsection*{Radial Distribution Functions}

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation 
	\item We obtain the best RDF by constructing splines that run through the
	pore centers.
	\item We construct the splines by dividing the membrane into 20 slices
	in the $z$-direction. Within each slice, we calculate the location of 
	the pore centers based on the average location of the aromatic rings
	that make up the monomer head groups.
	\item When calculating the RDF, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the ($x$, $y$)
	coordinates of appropriate point on the spline.
  \end{itemize}

  \subsubsection*{Coordination number}

  We quantified the coordination of solutes with surrounding molecules.
  \begin{itemize}
  	\item For each frame, we counted the identities and number of
  	coordinated molecules to a given solute based on a distance cut-off. 
	\item We found that this approach is more useful than calculating the
	3D spherical radial distribution function because it gives detailed
	frame-by-frame information rather than an average. 
  \end{itemize}

  \subsection{Experimental}
  % BJC: For Greg to write if things work out

  \section{Results and Discussion}

  \subsection{Governing Mechanisms}\label{section:mechanism_overview}

  % BJC: seems right to summarize overarching mechanisms observed first
  The mechanisms which govern transport of small polar solutes in this 
  system can be broadly described based a solute's size, shape, and polarity.
  \begin{itemize}
    \item In general, solutes can move fastest in the pore center, where
    there is comparatively little resistance to diffusion. 
  	\item The well-established trend of decreasing solute mobility with 
  	size is not defied here, however we observe small solutes with lower-than-expected
  	MSDs because they spend time trapped between monomer head groups.
  	\item Additionally, planar molecules are prone to exhibiting similar
  	trapping behavior, even for large molecules whose similar sized, but flexible
  	counterparts exhibit faster diffusion.  %BJC: this is unproven
  	\item The polarity of solutes also influences a solute's ability to stay in
  	the pore center. Highly polar molecules tend to spend more time in the pore center,
  	while those with hydrophobic character tend to spend more time in the head group
  	region.
  	\item Finally, the ability to hydrogen bond offers a second trapping mechanism. 
  	Solutes that are hydrogen bond donors can donate hydrogen atoms to
  	any of the 5 oxygen atoms located on the monomer head groups. Increasing the 
  	number of hydrogen bond donating groups increases the solute's polarity causing
  	solutes to spend more time in the pore centers, but the effect can be countered
  	by excessive trapping if there many hydrogen bonds are being formed.
  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
  	mechanisms, with anticorrelated hops between each period of immobility due to 
  	obstructions.
  \end{itemize}

  \end{itemize}

  We will explore these factors in greater detail in the context of 
  specific groups of molecules in the discussion that follows.

  \subsection{MSD Predictions}\label{section:msd_predictions}

  %BJC: focus on MD MSD results
  \noindent We calculated the MSD of each solute in the set over the course of 1$\mu$s MD simulations.  %BJC: type of MSD TBD 
  \begin{itemize}
	\item We extracted values of $\sigma$, $\alpha$ and $H$ for each solute
	and then simulated 10000 sFBM trajectories of the same length as our MD
	simulations, as described in Section~\ref{section:model_sFBM} of the Methods.
	\item The final MSDs of the sFBM trajectories are compared to those 
	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
	\item The three sFBM parameters, calculated based on MD solute trajectories
	are presented in Table~\ref{table:simulations}.
	\item We would like to emphasize that we rely on the MD MSD values in order to
	define trends in the total MSD, while the sFBM trajectories and parameter 
	values allow us to speculate as to the reasons for the observed trends. 
	\item There is a non-negligible amount of error in the calculation of 
	each parameter which prevents us from reliably portraying our sFBM MSDs as
	reduced	uncertainty MD MSDs.
  \end{itemize}

  Our simulated sFBM MSDs qualitatively reproduce the MD trends.
  \begin{itemize}
    \item sFBM generally lower
    \item There are a few noticeable discrepancies.
    \item We will discuss reasons for these as we proceed with the discussion.
  \end{itemize}

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{all_emsds.pdf}
  \caption{}\label{fig:all_msds}
  \end{figure}

  % Add MD calculated MSD to this?
  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System & $\sigma$ ($nm$) & $\alpha$ & $H$ \\
  \midrule
  Methanol & 0.46 & 0.85 & 0.40 \\
  Urea & 0.33 & 0.64 & 0.40 \\
  Ethylene Glycol & 0.35 & 0.64 & 0.36 \\
  Acetic Acid & 0.28 & 0.51 & 0.44 \\
  Mercaptoethanol & 0.30 & 0.54 & 0.26 \\
  Ethanol & 0.32 & 0.55 & 0.25 \\
  Propylene Glycol & 0.26 & 0.48 & 0.35 \\
  Glycerol & 0.23 & 0.46 & 0.37 \\
  Acetamide & 0.28 & 0.52 & 0.26 \\
  Propanol & 0.25 & 0.41 & 0.35 \\
  Acetone & 0.23 & 0.44 & 0.34 \\
  Ethyl Acetate & 0.21 & 0.41 & 0.37 \\
  Dimethyl Sulfoxide & 0.26 & 0.48 & 0.26 \\
  Tetrose & 0.24 & 0.43 & 0.30 \\
  Butanol & 0.19 & 0.41 & 0.33 \\
  Dimethyl Formamide & 0.20 & 0.39 & 0.32 \\
  2,3-Dimercapto-1-propanol & 0.20 & 0.37 & 0.35 \\
  Ribose & 0.20 & 0.40 & 0.27 \\
  Propylene Carbonate & 0.19 & 0.38 & 0.29 \\
  Tetrahydrofuran & 0.24 & 0.39 & 0.16 \\
  \bottomrule
  \end{tabular}
  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
  trajectories and then computed the average ensemble-averaged MSD of 10000 
  simulated trajectories.}\label{table:simulations}
  \end{table}

  It most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the
  simulated MSD values presented in Table~\ref{table:simulations}. 
  \begin{itemize}
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the simulated MSD
  \end{itemize}

  % BJC: figure with selected trajectories for each molecule.

  We fit a CTRW model (see Section~\ref{method:CTRW}) to these 
  trajectories and predicted macroscopic diffusion coefficients which are
  presented in Table TBD.
  \begin{itemize}
	\item We confirmed that our molecules exhibit anomalous diffusion
	by fitting a power law to the MSD curve. The exponent is less than
	1, indicative of anomalous subdiffusion.
	\item We used the decision making process given by Meroz and Sokolov
	in order to identify the appropriate subdiffusion model to use 
	based on our time series (See Section S-TBD of the Supporting info for
	more details).
	\item The motion of the solutes is non-ergodic and the steps are
	uncorrelated which tells us the system is likely well-described
	by a CTRW. 
  \end{itemize}

  % BJC: table with finalized diffusion coefficients

  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}

  Solutes in systems with lower water content exhibit lower diffusion coefficients.
  \begin{itemize}
	\item Pores are more crowded when there is less water (show RDFs of each)
	\item Not a linear function of pore size - radius increase by x, D increases by y
	\item Larger influence on bigger molecules
  \end{itemize}

  \subsubsection{Experimental Measurements}

  % For Greg

  \subsection{Transport Mechanisms}

  In order to truly understand the molecular origins of the macroscopic
  diffusion coefficients in Section~\ref{section:D_macro}, we studied the
  microscopic interactions between solutes and the membrane that lead to the
  observed dwell time and hop distributions.
  \begin{itemize}
	\item We studied the radial distribution functions of solutes as a
	function of distance from the pore center
	\item We looked at hydrogen bonding patterns
	\item Coordination numbers
	\item Order parameters
  \end{itemize}

  The radial distribution function of each solute studied is shown in 
  Figure TBD.

  \subsubsection*{Transport of Water}

  All water molecules exhibit hop diffusion.

  Even in the center of the pore, where the density of water molecules is
  highest, individual water molecules exhibit hop diffusion as they create a
  tight hydrogen bond network.
  %TODO: the following is a hypothesis
  \begin{itemize}
	\item Water sticks to pore walls
	\item Dwell times are short
	\item Water tumbles across pore for a while until it sticks again. 
	\item Water gets caught in h-bonds with other water molecules away
	from pore center.
  \end{itemize}

  In this confined environment, the diffusion constant is x times lower than
  expected bulk diffusion coefficient of tip3p water.

  %TODO: study diffusion mechanism of water

  \subsubsection*{Transport of Alcohols}

  The hydroxyl functional group of alcohol molecules is a hydrogen bond donor
  and prefers to donate it's hydrogen to more strongly polarized carboxylate head
  groups.

  As alcohol groups increase in hydrophobic character, they are more inclined
  to stick to the outside edges of the pore. 
  \begin{itemize}
	\item The alkane tails prefer to stay at the edges of the pore.
	\item Radial distribution functions show peaks at pore edges, however
	smaller alcohols have high densities near the pore center. 
	\item They tend to get trapped between monomers and closer to 
	the tail region. 
	\item The entrapment is further stabilized by hydrogen bonds with
	ether oxygens connecting the monomer's alkane tails to the head groups.
	%TODO: quantify h-bonds with ether oxygens and carbonyl oxygens
  \end{itemize}

  The diffusion coefficient of simple alcohols increases as the length of 
  the alkane chain increases.
  \begin{itemize}
	\item The dwell times increase as the oily tails become more
	entrapped in monomer tails.
  \end{itemize}

  Ethylene glycol, a diol, has two hydrogen bond donor groups.
  \begin{itemize}
	\item Can hydrogen bond with same moeity.
	\item Can hydrogen bond with different moeities in the same 
	vicinity. 
	\item Dwell times tend to be shorter. If one hydroxyl group is bound
	with a hydrogen bond, the other unbound hydroxyl group may form a hydrogen bond
	elsewhere and effectively pull the other bound hydroxyl group along with it. 
  \end{itemize}

  \subsubsection*{Transport of Acetone}

  The carbonyl group of Acetone is a hydrogen bond acceptor and therefore only
  form hydrogen bonds with water molecules in the pore.

  The hydrophobic character of the two methyl groups on acetone causes the methyl
  groups to gravitate towards the outside of the pore, while the carbonyl group
  reaches towards the pore center in order to hydrogen bond with water molecules.
  \begin{itemize}
	\item Order parameter defined between vector along carbonyl and vector extending
	from acetone COM to pore center is non-zero.
  \end{itemize}

  \subsubsection*{Transport of Acetic Acid}

  Acetic acid, since we modeled it solely in its protonated state, has hydrogen
  bond donor and acceptor groups.

  \subsubsection*{Transport of Ions} % probably just sodium

  Sodium ions also exhibit hop diffusion because polarized water and
  carboxylate head groups both work to neutralize its charge.
  \begin{itemize}
	\item Ions get trapped in oxygen 'cages' composed of combinations
	of water molecules, carboxylate head groups and ether oxygens connecting
	the head groups to their tails.
  	\item Interesting coordination number data
	\item Dwell time proportional to surrounding charge within coordination shell
  \end{itemize}

  \subsubsection*{Remarks}

  Overwhelming amount of water in 10 wt\% system makes hydrogen bonding
  competitive between head groups and water.
  %MRS: not sure what you mean above.

  \subsection{Design Suggestions}

  Water content affects pore size. Experiments to understand this could be useful.

  Separate polar molecules by creating monomers with more hydrophilic head group components.
  More incentive to dwell on walls.

  Make ions move faster by placing charges in sterically inaccessible places.

  \section{Conclusion}

  We have examined the transport characteristics of a series of small polar
  molecules in our model of the H\textsubscript{II} phase formed by 
  Na-GA3C11.

  We calculated the macroscopic diffusion coefficients of each solute as 
  approximated by a CTRW model and validated our estimates using experimental
  DOSY NMR measurements.

  We have studied the influence of water content on the diffusion coefficients.

  We showed that hydrogen bonding between solutes and Na-GA3C11 monomers plays
  a major role in mechanism by which molecules traverse the nanopores.

  We can use this intuition in order to modify our monomers for a specific 
  separation.
  \begin{itemize}
	\item Increase number of h-bond sites to increase selectivity towards water 
	over polar molecules
	\item Also separate acetone (things with only h-bond accepting groups) in this way
  \end{itemize}

  \section*{Supporting Information}

  Detailed explanations and expansions upon the results and procedures mentioned in
  the main text are described in the Supporting Information. This information is
  available free of charge via the Internet at http://pubs.acs.org.

  \section*{Acknowledgements}

  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  \clearpage

  \bibliographystyle{ieeetr}
  \bibliography{transport}

  \newpage

  \section*{TOC Graphic}

\end{document}

### 2019-06-28 Ben_Manuscripts/bcc/Outline.tex
Beginnings of BCC Manuscript

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

%BJC: potential titles (uncommented is current favorite)
\title{Understanding the nanoscopic structure of Q\textsubscript{I} phase LLC membranes}
\author{Benjamin J. Coscia \and Michael R. Shirts}

\begin{document}

  \graphicspath{{./figures/}}
  \maketitle

  \section{Introduction}

  We need highly selective membranes in order to perform efficient separations.

  Amphiphilic molecules are capable of self-assembling into ordered nanostructures.

  Lytropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
  into mechanically strong membranes.
  \begin{itemize}
  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
	sized pores and have the potential to disrupt conventional membrane separation
	techniques by being selective based not only on size and charge, but on chemical
	functionality as well.
	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
	pores.
  \end{itemize}

  We can only learn so much from experiment. MD can give us mechanistic insights with
  atomistic resolution so that we can intelligently design new membranes for 
  solute-specific separations.

  In our previous work, we studied the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane.

  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to predict macroscopic transport properties traditionally used to characterize
  membranes in the lab.

  % review of techniques for predicting long time scale behavior

  In this work, we have determined the transport mechanisms and macroscopic
  transport properties exhibited by a number of polar solutes with varying size,
  chemical functionality and hydrophilic character.
  \begin{itemize}
	\item Many of the separations we are interested in involve polar organic 
	compounds.
  \end{itemize}

  \section{Methods}

  \subsection{Molecular Dynamics Simulations}

  \subsubsection{Unit Cell Construction}\label{method:unit_cell}

  % BJC: These first 3 paragraphs might be better suited for introduction.
  The space group of the Q\textsubscript{I} phase configuration formed by
  the monomer 1 is thought to be either Pn3m or Ia3d.
  \begin{itemize}
    \item 6 Q phase architectures have been identified in small molecule
    amphiphile systems.~\cite{mariani_cubic_1988}
    \item Of these, only 4 are consistent with diffraction data generated
    by the gemini surfactant used here.~\cite{pindzola_cross-linked_2003}
    %BJC: excess detail for now
    \item Q$^{230}$ (Ia3d), Q$^{224}$ (Pn3m), Q$^{229}$ (Im3m) or Q$^{212}$ (P4\textsubscript{3}32) phase of type I configuration
    \item The presence of $1 / \sqrt{6}$ and $1 / \sqrt{8}$ peaks rules out the
    Q$^{227}$ (Fd3m) and Q$^{223}$ (Pm3n) configurations.
    \item The most likely phase is the type I Q$^{230}$ (Ia3d) because it is the
    most common phase observed between lamellar and hexagonal phases and the
    monomeric alkyltrimethylammonium salts used to synthesize the gemini LCs
    exhibit clear Ia3d symmetry. 
  \end{itemize}

  Molecular simulation studies of systems exhibiting bicontinuous cubic 
  phase behavior are typically centered around phase formation
  ~\cite{mondal_self-assembly_2013,ellison_entropy-driven_2006,gonzalez-segredo_coarsening_2004}
  and the few which study transport rely on a previously self-assembled unit cell.
  ~\cite{roy_water_2016}
  \begin{itemize}
    \item Self-assembly is a slow process which usually requires united atom
    or coarser molecular representations.~\cite{klein_large-scale_2008}
    \item Self-assembly also prevents us from creating unit cells with arbitrary
    space group symmetry since one space group is likely to be most energetically
    favorable for a given interaction potential.
    \item Therefore, we developed an initial configuration build procedure that allowed 
    us to place LLC monomers with Ia3d, Pn3m and any other symmetry. 
  \end{itemize}

  The interface between the hydrophilic and hydrophobic regions of Pn3m
  and Ia3d Q\textsubscript{I} unit cells can be described using triply-periodic
  minimal surfaces.~\cite{marrink_molecular_2001}  % This ref does what I do for monomer placement
  \begin{itemize}
	\item Schwarz' D surface describes the Pn3m interface while Schoen's gyroid
	describes the Ia3d interface.~\cite{hyde_bicontinuous_1996, andersson_minimal_1988}
	\item Both surfaces can be approximated using implicit trigonometric expressions:~\cite{von_schnering_nodal_1991}
	\item \begin{equation} 
	          sin(x)sin(y)sin(z) + sin(x)cos(y)cos(z) + cos(x)sin(y)cos(z) + cos(x)cos(y)sin(z) = C 
	      \label{eqn:schwarzD}
	      \end{equation}
	\item \begin{equation} 
	          sin(x)cos(y) + sin(y)cos(z) + sin(z)cos(x) = C 
	      \label{eqn:gyroid}
	      \end{equation}
	\item When $C$ = 0, the surface splits the unit cell into two equal volumes. % need reference if I'm actually going to say this
  \end{itemize}

  We find points that lie on the implicit surface and then place monomers
  perpendicular to the surface at those points.
  \begin{itemize}
    \item We placed 582 monomers at points on the desired surface of our unit
    cell based on the known experimental density, unit cell dimensions and 
    water content. % glycerol content? need to look this up again
    \item We identified points which lie close to the surface by creating a 
    cubic grid of points and only keeping those whose $(x, y, z)$ coordinates
    lie within a specified tolerance of C when substituted into 
    equation~ref{eqn:schwarD} or~\ref{eqn:gyroid}.
    \item We constructed a vector, $\mathbf{v}$, based on the monomer's constituent
    atom positions which points from the tails to the head groups.
    \item To place each monomer, we randomly chose one of the points on the surface, 
    translated a reference atom on the monomer to that point,
    and rotated the monomer so that $\mathbf{v}$ coincided with the vector normal
    to the surface, calculated based on the gradient of equations~\ref{eqn:schwarzD}
    and~\ref{eqn:gyroid}.
    \item After each monomer placement, we removed all grid points within a specified
    distance of the monomer in order to reduce overlaps in the initial configuration.
    \item This procedure shares similarities with that of Marrink and Tieleman.~\cite{marrink_molecular_2001} % BJC: Just found this reference :( I came up with this independently
  \end{itemize}

  Despite our best efforts, overlaps in our initial configuration were unavoidable
  since we used an all-atom model. 
  \begin{itemize}
    \item The simplest way to overcome this problem was to isotropically expand 
    the unit cell by doubling the unit cell vectors in all directions, increasing the unit
    cell volume by a factor of 8. 
    \item In a series of energy minimizations, we slowly shrank the unit cell
    back down to the desired size.
  \end{itemize}

  In accordance with experimental procedure, we solvated the unit cell with glycerol at
  70$^{\circ}$ C.
  \begin{itemize}
    \item We used the GROMACS command \texttt{gmx insert-molecules} to add the desired
    number of glycerol molecules to the unit cell.
    \item All of which were placed in the vacant pore region.
    \item In general, we could not insert all of the glycerol molecules intended in one try. 
    \item We performed a series of NVT simulations, inserting more glycerol molecules between
    each.
    \item Once we could no longer fit more glycerol molecules, we switched to the NPT
    ensemble and continued inserting glycerol molecules.
    \item We then allowed the system to equilibrate for an additional 5 ns.
  \end{itemize}

  % add glycerol to tails?

  Also in accordance with experimental preparation procedure, we cross-linked the 
  monoemr's diene tails at 70$^{\circ}$ C. 
  \begin{itemize}
    \item Practically, cross-linking is necessary for the membrane's mechanical
    integrity which likely will not have a significant influence on the timescales
    which we study. We include it anyways for consistency.
    \item Our cross-linking procedure is iterative. 
    \item Each iteration, we identify carbon atoms that are a part of the diene 
    tails and in close proximity.
    \item We update the topology to include new bonds and update atom types and
    other topological information accordingly.
    \item See Supporting Information for more details.
  \end{itemize}

  \section{Results and Discussion}

  \section{Conclusion}

  \section*{Supporting Information}

  Detailed explanations and expansions upon the results and procedures mentioned in
  the main text are described in the Supporting Information. This information is
  available free of charge via the Internet at http://pubs.acs.org.

  \section*{Acknowledgements}

  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  \clearpage

  \bibliographystyle{ieeetr}
  \bibliography{BCC}

  \newpage

  \section*{TOC Graphic}

\end{document}

### 2019-06-28 LLC_Membranes/setup/bcc_equil.py

@@ -378,6 +378,7 @@ if __name__ == "__main__":
 
     equil.build_initial_config(grid_points=args.grid, r=0.5)
     equil.scale_unit_cell(args.scale_factor)
+    exit()
 
     equil.generate_topology(name='topol.top')  # creates an output file
     equil.generate_mdps(length=50, frames=2, T=args.temperature)  # creates an object

### 2019-07-27 Ben_Manuscripts/stochastic_transport/Outline.tex
Incorporating iHMM

@@
 
-%BJC: potential titles (uncommented is current favorite)
-%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
-\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   Unfortunately, the timescales that we can simulate with MD are insufficient to be
-  able to predict macroscopic transport properties traditionally used to characterize
-  membranes in the lab.
+  able to predict well-converged predictions of macroscopic transport properties 
+  traditionally used to characterize membranes in the lab.
 
@@
 
-  In this work, we have determined the transport mechanisms and macroscopic
-  transport properties exhibited by a number of polar solutes with varying size,
-  chemical functionality and hydrophilic character.
+  In this work, we explore two approaches to modeling the dynamic behavior of 
+  a subset of solutes that we studied in our previous work.
   \begin{itemize}
-	\item Many of the separations we are interested in involve polar organic 
-	compounds.
+  	\item First is based on the anomalous diffusion literature
+  	\item Our second approach to modeling solute transport groups solute behavior
+    into different dynamical states.
+%  	\item Second focuses on the analysis of time series  % Need a better way to talk about it here 
   \end{itemize}
-
-  We have compared our calculated diffusion coefficients with experimental
-  measurements made using DOSY NMR.
 
@@
 
+  We ran all MD simulations and energy minimizations using GROMACS 2018. We
+  performed all post-simulation trajectory using python scripts which are available
+  online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
+
   \subsection{Molecular Dynamics Simulations}
 
-  \subsubsection*{System Setup}
-
-  There is a broad range of water concentrations which will form a stable 
-  H\textsubscript{II} phase with Na-GA3C11. 
+  We studied transport of solutes in the H\textsubscript{II} phase using an
+  atomistic molecular model of four pores in a monoclinic unit cell with 
+  10 \% water by weight. 
   \begin{itemize}
-	\item In the literature this system is typically synthesized with close
-	to 10 wt \% water
-    \item However, Resel et al. noted that the system is likely fully 
-	hydrated with less than 7 wt \% water.
-	\item We decided to test two different levels of water content: 5 and 10 wt \%
+    \item Approximately one third of the water molecules occupy the tail region 
+    with the rest near the pore center.
+    \item We chose to study the 10 wt \% water system because solutes move 
+    significantly faster than in the 5 wt \% system studied previously.
+    \item Appropriate stochastic modeling requires that solutes explore 
+    as much structural space as possible.  %BJC: better term than structural space?
   \end{itemize}
 
-  We observed that water partitions into the tail region of our system and therefore
-  built our initial configurations with water in both regions close to the expected
-  equilibrium value.
+  We chose to study a subset of 4 of the fastest moving solutes from our previous
+  work: methanol, acetic acid, urea and ethylene glycol.
   \begin{itemize} 
-	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
-	\item The amount of water present in the tails may or may not be experimentally consistent
-	but if we don't put it in, the results will not be thermodynamically consistent, which 
-	will give issues with measurements and calculations.
-	\item See supporting info for water equilibration simulation data.
-	\item We adjusted the pore radius in our systems so that the right amount of water
-	fits in the pores without any vacuum using \texttt{gmx solvate}.
-	\item We placed water molecules in the tail region one at a time in random locations
-	with short energy minimizations between insertions.
+    \item In addition to exploring membrane structural space the most, these solutes
+    have a relatively diverse set of chemical functionality.   
+    \item For each solute we created a separate system and to each system we
+    added 6 solutes per pore for a total of 24 solutes.
+    \item This number of solutes per pore provides a balance of a low 
+    degree of interaction between solutes and sufficient amount of data from
+    which to generate statistics on the time scales which we simulate.
+    \item Further details on the setup and equilibration of these systems can
+    be found in our previous work.\cite{coscia_chemically_2019}
   \end{itemize}
 
-%  We equilibrated the initial configuration using the `wet' equilibration procedure
-%  described in our previous work (reference to structure paper).
-  %BJC: not sure I need to go into any details describing that procedure
-%  \begin{itemize}
-%	\item Series of NVT simulations with force constants on carbon atoms of aromatic
-%	ring in head group
-%	\item Force constants reduced according to the sequence: 1000000, 3162,
-%	56, 8, 3, 2, 1, 0 kJ mol$^{-1}$ nm$^{-2}$ 
-%  \end{itemize}
-
-%  We cross-linked the equilibrated solvated configuration using the cross-linking procedure
-%  described in our previous work.
-
-  We equilibrated an initial solvated configuration before adding solutes.
+  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
+  to collect ample data.
   \begin{itemize}
-	\item We equilibrated the initial configuration using the `wet'
-	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
-	\item We cross-linked the equilibrated solvated configuration using the
-	cross-linking procedure described in our previous work. 
+    \item We simulated the system with a time step of 2 fs at a pressure of 1 bar
+    and 300 K controlled by the Parinello-Rahman barostat and the v-rescale thermostat
+    respectively.
   \end{itemize}
 
-  We added 6 solute molecules to each pore of the equilibrated cross-linked
-  configuration.
-  \begin{itemize}
-	\item We equally spaced each solute in the pore
-	\item 6 solutes per pore provided a balance of a useful amount of data
-	for generating statistics and a low degree of interaction between solutes (reference
-	to supporting information to show low degree of interaction)
-	\item At each insertion point we placed a randomly oriented solute molecule
-	then ran a short energy minimzation.
-	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
-	pressure control
-	\item We collected transport data using long simulations, on the order of
-	1 microsecond
-	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
-  \end{itemize}
+  \subsection{Modeling subdiffusion}\label{method:model_sFBM}
 
-  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}
-
-  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
+  Solutes in our H\textsubscript{II} LLC membrane system exhibit subdiffusive
   behavior, a type of anomalous diffusion.
@@
 	generalized diffusion coefficient.
-	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
-	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
+	\item A value of $\alpha < 1$ indicates a subdiffusive process, while values of
+	$\alpha = 1$ and $\alpha > 0$ are characteristic of Brownian and superdiffusive
 	motion respectively.
@@
 
-  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
+  \noindent We analyzed both the ensemble-averaged and time-averaged MSDs
   of the simulated trajectories.
@@
 	trajectory~\cite{meroz_toolbox_2015}. 
-%	\item The time-averaged MSD becomes linear in our simulations,
-%	therefore we can fit a line to its slope in order to estimate the macroscopic
-%	diffusivity of the particle.
-	%BJC: this needs more justification. Not many people have done it
-	%BJC: could also not report them as diffusivities. Comparison of total MSD
-	% should give same information
-	% Linear region probably exists because dwell times on the order of large lag times
-	% become negligible
   \end{itemize}
 
-  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
-  continuous time random walks (CTRW), fractional Brownian motion (FBM) and
-  random walks on fractals (RWF).\cite{meroz_toolbox_2015}
+  \noindent Three common mathematical models for modeling anomalous subdiffusion
+  processes include continuous time random walks (CTRW), fractional Brownian motion
+  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
   \begin{itemize}
@@
 
+  % BJC: Should this be in the results?
   \noindent We believe that solutes in the system studied here exhibit subordinated 
@@
 	\item We used the \texttt{ruptures} python package in order to identify
-	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
-	details on chosen parameters. i.e. type of cost function, cost function penalty
-	tolerance, number of dimensions used)
-	\item The corresponding hop lengths and dwell times between break points were 
-	used to construct empirical distributions.
-	\item For solutes in our system, the distribution of hop lengths is
+	changepoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting
+	Information for more details on chosen parameters. i.e. type of cost function, 
+	cost function penalty tolerance, number of dimensions used)
+	\item We used the corresponding hop lengths and dwell times between break points
+	to construct empirical distributions.
+  \end{itemize}
+
+  For solutes in our system, the distribution of hop lengths appears to be
   well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
   metzler_anomalous_2014,neusius_subdiffusion_2009}
+  \begin{itemize}
 	\item We are most interested in the standard deviation, $\sigma$, of the 
 	hop length distribution.
-	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
+  \end{itemize}
+
+  The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
   distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
+  \begin{itemize}
 	\item Because we are limited to taking measurements at discrete values
@@
 
+  In general, we observe different dynamical behavior when solutes move inside the
+  pore versus in the tail region.
+  \begin{itemize}
+    \item Therefore, we created 2 sets of parameters based on the solute's radial location.
+    \item Solutes in the pore region are located less than 0.75 nm from the pore center and
+    all else are in the tail region. 
+    \item We determined this cut-off and described how we calculated radial 
+    distance from the pore center in our previous work~\cite{coscia_chemically_2019}
+  \end{itemize}
+
 %  We generated distributions of parameters for the dwell time and hop length
@@
 %  magnitude longer than our molecular simulations.
-  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
+  \noindent For each solute, we simulated 10000 5 $\mu$s sFBM trajectories. 
   \begin{itemize}
@@
 	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
-	the last data point so that the total time exactly equaled 1 $\mu$s. 
+	the last data point so that the total time exactly equaled 5 $\mu$s. 
     \item Valid comparisons are only possible between fixed length sFBM simulations. The
@@
     a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
-    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
+    \item We reported the MSD after 5 $\mu$s with corresponding 95 \% intervals
 % Following probably better suited for supporting information, if included at all
@@
 
-  \subsubsection*{Radial Distribution Functions}
+%  \subsubsection*{Coordination number}
 
-  We measured the average radial distance of each solute of interest from the pore
-  centers.
+%  We quantified the coordination of solutes with surrounding molecules.
+%  \begin{itemize}
+%  	\item For each frame, we counted the identities and number of
+%  	coordinated molecules to a given solute based on a distance cut-off. 
+%	\item We found that this approach is more useful than calculating the
+%	3D spherical radial distribution function because it gives detailed
+%	frame-by-frame information rather than an average. 
+%  \end{itemize}
+
+  \subsection{The Infinite State Hidden Markov Model}
+
+  Hidden Markov models (HMMs) are a useful and widely used technique
+  for modeling sequences of observations where the probability of the next observation
+  in a sequence depends only on a previous unobserved, or hidden, state.~\cite{beal_infinite_2002}
   \begin{itemize}
-	\item We binned the radial distances and then normalized by the volume
-	of the annulus defined by the bin edges.
-	\item Although the pores are often described as straight, they have a
-	small degree of tortuosity which disrupts the RDF calcuation 
-	\item We obtain the best RDF by constructing splines that run through the
-	pore centers.
-	\item We construct the splines by dividing the membrane into 20 slices
-	in the $z$-direction. Within each slice, we calculate the location of 
-	the pore centers based on the average location of the aromatic rings
-	that make up the monomer head groups.
-	\item When calculating the RDF, the radial distance from the pore center
-	is based on the distance between the solute center-of-mass and the ($x$, $y$)
-	coordinates of appropriate point on the spline.
+    \item In the context of our simulations, the observations correspond to 
+    the center of mass coordinates of the solutes versus time, and the states
+    correspond to the dynamical behavior which giving rise to those types
+    of observations.
+    \item Unfortunately, HMMs require the number of hidden states to be known
+    a priori.
   \end{itemize}
 
-  \subsubsection*{Coordination number}
-
-  We quantified the coordination of solutes with surrounding molecules.
+  The infinite-state HMM overcomes this drawback using a hierarchical
+  Dirichlet process (HDP).
   \begin{itemize}
-  	\item For each frame, we counted the identities and number of
-  	coordinated molecules to a given solute based on a distance cut-off. 
-	\item We found that this approach is more useful than calculating the
-	3D spherical radial distribution function because it gives detailed
-	frame-by-frame information rather than an average. 
+    \item Using some base probability distribution, H, a Dirichlet process 
+    (DP) generates distributions over a countably infinite number of 
+    probability measures:
+    \begin{equation}
+      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H
+    \end{equation}
   \end{itemize}
-
-  \subsection{Experimental}
-  % BJC: For Greg to write if things work out
 
@@
   	obstructions.
-  \end{itemize}
-
   \end{itemize}
@@
   \bibliographystyle{ieeetr}
-  \bibliography{transport}
+  \bibliography{stochastic_transport}
 

### 2019-08-15 Ben_Manuscripts/stochastic_transport/Outline.tex
Methods and discussion additions

@@
   \section{Introduction}
-
+  %BJC: obviously this section will get beefed up
   We need highly selective membranes in order to perform efficient separations.
 
-  Amphiphilic molecules are capable of self-assembling into ordered nanostructures.
+  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.
 
@@
 	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
-	pores.
+	pores. They are easier to make.
   \end{itemize}
@@
   in an H\textsubscript{II} phase LLC membrane.
+  \begin{itemize}
+    \item In general, we observed subdiffusive transport behavior characterized 
+    by intermittent hops separated by periods of entrapment.
+    \item We identified three mechanisms responsible for the solute trapping behavior:
+    entanglement among monomer tails, hydrogen bonding with monomer head groups, and
+    association with sodium counter ions.
+  \end{itemize}
 
+  % BJC: I've been trying to understand the following justification a bit more. Does it
+  % rely on the MSD becoming linear so we can get experimentally diffusion constants? Is
+  % it just to try and reduce uncertainty in our MSD predictions? What can we learn from
+  % long stochastic simulations that we can't learn from the shorter simulations.
+  % BJC: To me the value in this is gaining a deeper mechanistic understanding by 
+  % putting things in terms of easily interpreted equations.
+  % BJC: Maybe it's just a combination of both.
   Unfortunately, the timescales that we can simulate with MD are insufficient to be
-  able to predict well-converged predictions of macroscopic transport properties 
+  able to make well-converged predictions of macroscopic transport properties 
   traditionally used to characterize membranes in the lab.
 
-  % review of techniques for predicting long time scale behavior
+  One can draw from a number of scientific field to model transport behavior as a
+  stochastic process.
+  \begin{itemize}
+    \item In the simulation literature, most start with mean squared displacement (MSD)
+    \item Due to the time scales most people simulate, the MSD does not give a complete
+    picture of what happens long-term.
+    \item Markov state models are popular with researchers of proteins which have 
+    many dynamical states occurring over multiple time scales.
+    \item The anomalous diffusion literature 
+    \item The financial literature studies a wide range of time series behavior which 
+    may be particularly useful for describing short time scale dynamics.
+  \end{itemize}
 
-  In this work, we explore two approaches to modeling the dynamic behavior of 
-  a subset of solutes that we studied in our previous work.
+  % brief (1 paragraph) review of techniques for predicting long time scale behavior
+  The are numerous ways one can approach modeling transport behavior, withing varying
+  levels of complexity.
   \begin{itemize}
-  	\item First is based on the anomalous diffusion literature
-  	\item Our second approach to modeling solute transport groups solute behavior
-    into different dynamical states.
-%  	\item Second focuses on the analysis of time series  % Need a better way to talk about it here 
+    \item Most
+
+    \item Mean first passage time?
+
+    \item Hidden markov models are useful for when states are known but one cannot
+  \end{itemize}
+  % Ornstein-Uhlenbeck (Gaussian + non-Gaussian)
+
+  Talk about finance, single particle tracking and other places this type of analysis
+  are used. Use word ubiquitous
+
+  In this work, we explore three approaches to model the long timescale behavior
+  of the four solutes fasted moving solutes studied in our previous work.
+  \begin{itemize}
+    \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
+  	\item Our first approach is based on the anomalous diffusion literature.
+  	\item The second approach uses Markov state models (MSMs) 
+  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
+  	learning algorithm which groups solute behavior into different dynamical states.
+  	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
+  	% require anything different in systems with more complex geometries (i.e. QI)
   \end{itemize}
@@
 
+  \subsection{Markov State Models}\label{method:MSMs}  % BJC: this section first in hopes that sfbm works better
+
+  A Markov state model decomposes a time series into a set of discrete states
+  with transitions between states defined by a transition probability matrix, T,
+  which describes the conditional probability of jumping to a specific 
+  state given the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
+  \begin{itemize}
+    \item In the context of molecular simulations, MSMs are frequently used
+    to study systems with slow dynamics, such as protein folding.~\cite{snow_how_2005,chodera_automatic_2007}
+    \item Researchers typically aim to come up with a low dimensional 
+    representation of the system based on features which preserve the process
+    kinetics. This facilitates the identification of discrete states from
+    which T is generated.
+    \item Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011}
+    and pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable 
+    of featurization and dimensional reduction.
+  \end{itemize}
+
+  In this work, we define a total of 8 discrete states based on the 3 trapping
+  mechanisms observed in our previous work. 
+  \begin{itemize}
+  	\item Therefore, there is no need to subject our trajectories to any reduction
+  	in dimensionality. 
+  	%BJC: not sure the best way to lay these out
+  	\item The states we've chosen include all combinations of trapping mechanisms 
+  	in the pore and out of the pore:
+  	\begin{enumerate}
+  	  \item Trapped in tails
+  	  \item Trapped in tails and hydrogen bonding
+  	  \item Trapped in tails and associated with sodium
+  	  \item Trapped in tails, hydrogen bonding and associated
+  	  \item In pores
+  	  \item In pores and hydrogen bonding
+  	  \item In pores and associated with sodium
+  	  \item In pores, hydrogen bonding and associated
+  	\end{enumerate}
+  	\item These choices assume that there are no significant kinetic effects resulting
+  	from solute conformational changes or pore size fluctuations, an assumption 
+  	that may be relaxed in future work.
+  	\item However, we will adopt the validation techniques used in the packages
+  	mentioned above.  
+  \end{itemize}
+
+  % BJC: does it make sense to use Dirichlet Process as a conjugate prior for
+  % getting error on transition matrix?
+
+  \noindent We constructed a state transition probability matrix based on observed solute
+  trajectories.
+  \begin{itemize}
+    \item Using methods described in our previous work, we determined 	
+    which, if any, trapping mechanisms affected the solute at each time step, and
+    assigned the observation to a specific state according to the definitions 
+    above.~\cite{coscia_chemically_2019}
+    \item Based on the current and previous state observation, we incremented the
+    appropriate entry of an $n x n$ count matrix by 1, where $n$ is the number of states.
+    \item For example, if we observed state 1 followed by a transition to state 3,
+    we increment the $(1, 3)$ entry of the count matrix by 1.
+    \item We generate the transition probability matrix from the count matrix by 
+    normalizing the entries in each row so that they summed to unity.
+  \end{itemize}
+
+  \noindent We recorded the $z$-direction displacement at each time step in order to construct
+  individual emission distributions for each state and transition between states.
+  \begin{itemize}
+    \item While the dynamics of the states themselves are important, the 
+    majority of observations involve transitions between states, so properly modeling
+    the transition dynamics is even more important.
+    %BJC: some of the transitions are pretty rare, so those emission distributions might be less reliable
+    \item The shape of the distributions are symmetric and heavy-tailed. 
+  \end{itemize}
+
+  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
+  \begin{itemize}
+    \item For independent and identically distributed (iid) random variables, the 
+    generalized central limit theorem guarantees convergence of the associated 
+    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
+    % BJC: ``For sums of independent, iid random variables with proper normalization to the
+%    sample size, the generalized central limit theorem guarantees the convergence of
+%    the associated PDF to a L\'evy stable PDF even though the variance of these random
+%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
+    \item The characteristic equation describing the Fourier transform of a L\'evy 
+    stable PDF is given below:
+    \begin{equation}
+    p_{\alpha, \beta}(k;\mu,\sigma) = exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
+    \end{equation}
+    \item Where $\omega$ is defined with something that is complicated to format and can be 
+    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
+    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
+    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
+    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
+    functions, is the Gaussian PDF ($\alpha$ = 2).
+    \item The more general family of L\'evy stable distributions allows
+    greater flexibility in defining the observed emission distribution PDFs.
+    \item In the case that the empirical emission distributions are iid, sequential draws
+    from a L\'evy stable PDF defines a L\'evy process. 
+    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
+    probability distributions if we instead consider the dynamics to be governed by a
+    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
+    \item OU processes contain temporal dependence but the marginal observation distributions
+    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
+    \item We will discuss the implications of each.  
+  \end{itemize}
+
+  L\'evy stable distributions often have heavy tails and an undefined variance 
+  which can give rise to arbitrarily long particle displacements.
+  \begin{itemize}
+  	\item We do not observe hops longer than x nm in our simulations which 
+  	emphasizes that these distributions are only an approximation.
+    \item We avoid unrealistic, enormous hops problem by truncating the tails
+    of the distribution. %BJC: can add some citations about truncated Levy distributions
+    \item Since solutes in our system cannot hop further than the length of our 
+    simulation unit cell, we truncate the tails of the distribution at this
+    magnitude.
+    % BJC: Is this actually the right way to do this? I am looking at unwrapped coordinates,
+    % so theoretically a particle can move as far as it wants between frames.
+    % BJC: The cut-off choice is pretty important and has a significant effect on MSD. 
+    % For example, if I truncate at the unit cell length I reproducably get a final MSD of ~ 66 nm^2 (1000 ns stochastic simulation)
+    % If I truncate the tails at double the unit cell length, I get a final MSD of ~107 nm^2
+    % The uncertainty also increases (since variance diverges for these distributions)
+    % So maybe it makes the most sense to truncate based on largest observed hops.
+  \end{itemize}
+
+  We simulated realizations of the stochastic process using the probability transition
+  matrix and emission distributions.
+  \begin{itemize}
+    \item For each trajectory simulated, we chose an in initial state randomly from a 
+    uniform distribution.
+%BJC: could construct initial distribution but I'm not sure how reliable that is based on 24 solutes that are started in the pore center.
+(need to chop off beginning 5 ns or so to get rid of that initial dependence)
+    \item We randomly drew subsequent state transitions and corresponding emissions 
+    from the rows of the probability transition matrix and the appropriate emission
+    distribution respectively.
+  \end{itemize}
+
+  %BJC: need to add some validation of Markovian behavior and time step choice.
+
   \subsection{Modeling subdiffusion}\label{method:model_sFBM}
 
-  Solutes in our H\textsubscript{II} LLC membrane system exhibit subdiffusive
-  behavior, a type of anomalous diffusion.
+  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
   \begin{itemize}
@@
 	\begin{equation}
-	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
+	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle^2
 	\label{eqn:ensemble_msd}
@@
 
-  % BJC: Should this be in the results?
+  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
   \noindent We believe that solutes in the system studied here exhibit subordinated 
@@
   	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
-  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
+  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}  % BJC: need a figure to show this
   	\item We also observe non-stationary $z$-coordinate traces of each solute's
@@
   \noindent We can characterize a CTRW process using the parameters which describe its
-  dwell time and hop length distribution.
+  dwell time and hop length distribution.  % This is different from the emissions of the markov state model where every single step is used to construct the distribution. 
   \begin{itemize}
@@
 
-  The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
+  \noindent The distribution of dwell times is expected to fit a power law
   distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
@@
 
+  % BJC: Is it worth showing performance of both types of models? one mode versus two mode?
+  % Probably worth showing that 1 state fails
+  % BJC: also not sure if there is a better word than mode. I stayed away from 'state' since
+  % it's used heavily in the MSM section.
+  % BJC: I haven't created the 2 mode model yet, but that'll only take a few hours. I'll
+  % do that after I get BCC equilibrations running
   In general, we observe different dynamical behavior when solutes move inside the
@@
   \begin{itemize}
-    \item Therefore, we created 2 sets of parameters based on the solute's radial location.
-    \item Solutes in the pore region are located less than 0.75 nm from the pore center and
-    all else are in the tail region. 
+    \item This inspired two models of varying complexity.
+    \item We created a simple, single mode model with a single $\alpha$, $\sigma$ and $H$
+    parameter fit to each solute.
+    \item Our second, two mode model assigns a set of parameters to each of 2 modes based
+    on the solute's radial location.
+    \item Solutes in mode 1 are in the pore region defined as less than 0.75 nm from any
+    pore center and all else are in mode 2, the tail region. 
     \item We determined this cut-off and described how we calculated radial 
@@
 
-  \subsection{The Infinite State Hidden Markov Model}
+  \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}  %BJC: potentially a separate paper
 
@@
     the center of mass coordinates of the solutes versus time, and the states
-    correspond to the dynamical behavior which giving rise to those types
+    correspond to the dynamical behavior which give rise to those types
     of observations.
-    \item Unfortunately, HMMs require the number of hidden states to be known
+    \item Unfortunately, standard HMMs require the number of hidden states to be known
     a priori.
@@
 
-  The infinite-state HMM overcomes this drawback using a hierarchical
-  Dirichlet process (HDP).
+  The infinite-state HMM overcomes this drawback by placing a hierarchical
+  Dirichlet process (HDP) prior on the transition probabilities.
   \begin{itemize}
@@
     \begin{equation}
-      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H
+      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
     \end{equation}
+    where the $\theta_k$ are values drawn from the base distribution and the
+    weights $\beta_k$ come from a stick-breaking process parameterized by the concentration 
+    parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). 
+    \item The concentration parameter expresses one's confidence in H relative to the posterior 
+    and is closely related to the number of data observations.
+    \item Each row, $G_j$, of the transition matrix is produced by drawing from a DP specified 
+    using the $\beta$ vector as a discrete base distribution and a separate concentration
+    parameter, $\alpha$.
+    \begin{equation}
+      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
+    \end{equation}
+    \item This hierarchical specification ensures that the transition probabilities in 
+    each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
   \end{itemize}
 
+  \noindent We describe the dynamics of each state using a vector autoregressive (VAR) model. 
+  \begin{itemize}
+  	\item A VAR process is characterized by a vector of observations in a time series 
+  	that are dependent on $r$ previous values of the time series vector, weighted by a
+  	coefficient matrix $A_i$ in addition to a white noise term $\mathbf{e}_t$:
+  	\begin{equation}
+  	\mathbf{y}_t = \sum_{i=1}^r A_i\mathbf{y}_{t-i} + \mathbf{e}_t~~~~\mathbf{e}_t \sim N(0, \Sigma)
+  	\end{equation}
+  	\item We assumed multivariate Gaussian noise and limited our analysis to an 
+  	autoregressive order of $r=1$.
+  	\item We used a conjugate matrix-normal inverse-Wishart prior on parameters
+  	$A$ and $\Sigma$ in order to analytically draw from the posterior.
+  \end{itemize}
+
+  Based on the VAR parameters and matrix of transition probabilities, we calculated
+  the most likely sequence of hidden states.
+  \begin{itemize}
+    \item We repeated this process iteratively until we reached convergence % BJC: need to define convergence criteria
+    \item Our python implementation of this process is heavily adapted from the MATLAB code
+    of Fox et al.~\cite{fox_sticky_2007} 
+    \item We refer the interested reader to much more extensive descriptions of 
+    this process and its implementation. 
+    ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
+  \end{itemize}
+  \break
   \section{Results and Discussion}
 
-  \subsection{Governing Mechanisms}\label{section:mechanism_overview}
+  \subsection{Molecular Dynamics Simulations}\label{section:MD_simulations}
 
-  % BJC: seems right to summarize overarching mechanisms observed first
-  The mechanisms which govern transport of small polar solutes in this 
-  system can be broadly described based a solute's size, shape, and polarity.
+  The MSDs for of the solutes calculated from 5 $\mu s$ MD simulation trajectories
+  are shown in Figure TBD.
   \begin{itemize}
-    \item In general, solutes can move fastest in the pore center, where
-    there is comparatively little resistance to diffusion. 
-  	\item The well-established trend of decreasing solute mobility with 
-  	size is not defied here, however we observe small solutes with lower-than-expected
-  	MSDs because they spend time trapped between monomer head groups.
-  	\item Additionally, planar molecules are prone to exhibiting similar
-  	trapping behavior, even for large molecules whose similar sized, but flexible
-  	counterparts exhibit faster diffusion.  %BJC: this is unproven
-  	\item The polarity of solutes also influences a solute's ability to stay in
-  	the pore center. Highly polar molecules tend to spend more time in the pore center,
-  	while those with hydrophobic character tend to spend more time in the head group
-  	region.
-  	\item Finally, the ability to hydrogen bond offers a second trapping mechanism. 
-  	Solutes that are hydrogen bond donors can donate hydrogen atoms to
-  	any of the 5 oxygen atoms located on the monomer head groups. Increasing the 
-  	number of hydrogen bond donating groups increases the solute's polarity causing
-  	solutes to spend more time in the pore centers, but the effect can be countered
-  	by excessive trapping if there many hydrogen bonds are being formed.
-  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
-  	mechanisms, with anticorrelated hops between each period of immobility due to 
-  	obstructions.
+    \item 2 options for a figure:
+    \item 1) 2 panels: 1st panel: bar chart with final MSD value + error bars. 2nd panel: a selected MSD curve
+    \item 2) 1 panel. All MSD curves. Overlapping errors might look bad
   \end{itemize}
 
-  We will explore these factors in greater detail in the context of 
-  specific groups of molecules in the discussion that follows.
-
-  \subsection{MSD Predictions}\label{section:msd_predictions}
-
-  %BJC: focus on MD MSD results
-  \noindent We calculated the MSD of each solute in the set over the course of 1$\mu$s MD simulations.  %BJC: type of MSD TBD 
+  Solute motion is influenced by the same three trapping mechanisms observed in our
+  previous works.
   \begin{itemize}
-	\item We extracted values of $\sigma$, $\alpha$ and $H$ for each solute
-	and then simulated 10000 sFBM trajectories of the same length as our MD
-	simulations, as described in Section~\ref{section:model_sFBM} of the Methods.
-	\item The final MSDs of the sFBM trajectories are compared to those 
-	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
-	\item The three sFBM parameters, calculated based on MD solute trajectories
-	are presented in Table~\ref{table:simulations}.
-	\item We would like to emphasize that we rely on the MD MSD values in order to
-	define trends in the total MSD, while the sFBM trajectories and parameter 
-	values allow us to speculate as to the reasons for the observed trends. 
-	\item There is a non-negligible amount of error in the calculation of 
-	each parameter which prevents us from reliably portraying our sFBM MSDs as
-	reduced	uncertainty MD MSDs.
+    \item The extent to which each trapping mechanism influences each solute is
+  depicted graphically in Figure TBD.
+    \item Same types of figures from transport paper:
+    \item Fraction participating in hydrogen bonds, fraction associated, fraction
+    in the tails.
+    \item Lifetimes of hbonds and sodium associations?
   \end{itemize}
 
-  Our simulated sFBM MSDs qualitatively reproduce the MD trends.
+  \subsection{Markov State Model Fits}\label{section:msm_results}
+
+  The emission distributions are non-Gaussian and heavy-tailed (see Figure~\ref{fig:emissions_MET}).
   \begin{itemize}
-    \item sFBM generally lower
-    \item There are a few noticeable discrepancies.
-    \item We will discuss reasons for these as we proceed with the discussion.
+    \item The heavy tails of the distribution are a consequence of hopping.
+    \item Heavily sampled states fit well to L\'evy stable distributions.
+    \item The rarer states have less data, but we still assume L\'evy stable distributions.
   \end{itemize}
 
-  \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{all_emsds.pdf}
-  \caption{}\label{fig:all_msds}
+  % BJC: worth proving these are non-Gaussian? One might argue that they look Gaussian but they are not at all.
+  \begin{figure}[!h]
+  \includegraphics[width=\textwidth]{emissions_MET.pdf}
+  \caption{}\label{fig:emissions_MET}
   \end{figure}
 
-  % Add MD calculated MSD to this?
+  % BJC: need better or more descriptive way of describing stochastic simulations
+  % BJC: or could say that whenever we say simulations, we mean stochastic simulations unless it is specified as a molecular dynamics simulation.
+  Simulating solute trajectories (see Section~\ref{method:MSMs}) by drawing independent  
+  observations from the emission distributions yields near linear MSD curves
+  with final values that are far higher than those observed in our molecular simulations.
+  \begin{itemize}
+	% BJC: right number of solute trajectories to simulate for comparison? More tightens the error bars
+    \item In the case of methanol, the final MSD value is about 25x higher than that observed in our
+    previous transport study (see Figure~\ref{fig:msd_MET}).
+    \item The linear behavior of the MSD curve is not consistent with subdiffusion.
+  \end{itemize}
+
+  \begin{figure}[!h]
+  \includegraphics[width=\textwidth]{MET_msd.pdf}
+  \caption{}\label{fig:msd_MET}
+  \end{figure}
+
+  Anti-correlation between hops may be responsible for subdiffusive behavior.
+  \begin{itemize}
+    \item In general, we observe negative correlation between hops.
+    \item A L\'evy driven OU process may be a more appropriate way to model
+    the stochastic dynamics of this system since you can incorporate autocorrelation.
+    \item Extracting reliable correlation functions is difficult with our data
+    due to relatively frequent switching resulting in sets of short disjoint time 
+    series describing each state.
+    \item Therefore we did not do this and attempted to fit a different model. 
+    %BJC: we could add some artificial correlation to test the anti-correlation hypothesis
+  \end{itemize}
+
+  \subsection{Subordinated Fractional Brownian Motion Modeling}\label{section:sFBM}
+
+  Using the techniques from Section~\ref{section:model_sFBM}, we extracted values 
+  of $\sigma$, $\alpha$ and $H$ for each solute for the 1 and 2 mode model 
+  (see Table~\ref{table:sfbm_params}).
+  \begin{itemize}
+    \item In most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the
+    simulated MSD values presented in Table~\ref{table:simulations}. 
+  	\item Higher values of $\sigma$ indicate larger average hop lengths.
+  	\item Higher values of $\alpha$ mean that there will be less sampling of 
+  	long dwell times.
+  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
+  	of anti-correlation.
+  	\item All of which contribute to an overall increase in the MSD.
+  \end{itemize}
+
+  % BJC: worth including single parameter model (i.e. no radial dependence) to 
+  % show its shortcomings? Or send to supporting information
+  % BJC: obviously still needs 2 mode data
   \begin{table}[h]
@@
   Acetic Acid & 0.28 & 0.51 & 0.44 \\
-  Mercaptoethanol & 0.30 & 0.54 & 0.26 \\
-  Ethanol & 0.32 & 0.55 & 0.25 \\
-  Propylene Glycol & 0.26 & 0.48 & 0.35 \\
-  Glycerol & 0.23 & 0.46 & 0.37 \\
-  Acetamide & 0.28 & 0.52 & 0.26 \\
-  Propanol & 0.25 & 0.41 & 0.35 \\
-  Acetone & 0.23 & 0.44 & 0.34 \\
-  Ethyl Acetate & 0.21 & 0.41 & 0.37 \\
-  Dimethyl Sulfoxide & 0.26 & 0.48 & 0.26 \\
-  Tetrose & 0.24 & 0.43 & 0.30 \\
-  Butanol & 0.19 & 0.41 & 0.33 \\
-  Dimethyl Formamide & 0.20 & 0.39 & 0.32 \\
-  2,3-Dimercapto-1-propanol & 0.20 & 0.37 & 0.35 \\
-  Ribose & 0.20 & 0.40 & 0.27 \\
-  Propylene Carbonate & 0.19 & 0.38 & 0.29 \\
-  Tetrahydrofuran & 0.24 & 0.39 & 0.16 \\
   \bottomrule
@@
   trajectories and then computed the average ensemble-averaged MSD of 10000 
-  simulated trajectories.}\label{table:simulations}
+  simulated trajectories.}\label{table:sfbm_params}
   \end{table}
 
-  It most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the
-  simulated MSD values presented in Table~\ref{table:simulations}. 
+  \noindent We compared the MSD of simulated sFBM trajectories to MD simulated
+  MSDs.
   \begin{itemize}
-  	\item Higher values of $\sigma$ indicate larger average hop lengths.
-  	\item Higher values of $\alpha$ mean that there will be less sampling of 
-  	long dwell times.
-  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
-  	of anti-correlation.
-  	\item All of which contribute to an overall increase in the simulated MSD
+	\item We simulated 10000 sFBM trajectories of the same length as our MD
+	simulations, as described in Section~\ref{section:model_sFBM} of the Methods.
+	\item The final MSDs of the sFBM trajectories are compared to those 
+	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
+	\item We would like to emphasize that we rely on the MD MSD values in order to
+	define trends in the total MSD, while the sFBM trajectories and parameter 
+	values allow us to speculate as to the reasons for the observed trends. 
+	\item There is a non-negligible amount of error in the calculation of 
+	each parameter which prevents us from reliably portraying our sFBM MSDs as
+	reduced	uncertainty MD MSDs.
+	% BJC: I think it's more the power law tails that increases uncertainty.
   \end{itemize}
 
-  % BJC: figure with selected trajectories for each molecule.
-
-  We fit a CTRW model (see Section~\ref{method:CTRW}) to these 
-  trajectories and predicted macroscopic diffusion coefficients which are
-  presented in Table TBD.
+  The two-mode sFBM model does a better job than the one-mode model at 
+  reproducing the MD MSD trends. 
   \begin{itemize}
-	\item We confirmed that our molecules exhibit anomalous diffusion
-	by fitting a power law to the MSD curve. The exponent is less than
-	1, indicative of anomalous subdiffusion.
-	\item We used the decision making process given by Meroz and Sokolov
-	in order to identify the appropriate subdiffusion model to use 
-	based on our time series (See Section S-TBD of the Supporting info for
-	more details).
-	\item The motion of the solutes is non-ergodic and the steps are
-	uncorrelated which tells us the system is likely well-described
-	by a CTRW. 
+    \item One-mode model generally undershoots MSDs.
   \end{itemize}
 
-  % BJC: table with finalized diffusion coefficients
-
-  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}
-
-  Solutes in systems with lower water content exhibit lower diffusion coefficients.
-  \begin{itemize}
-	\item Pores are more crowded when there is less water (show RDFs of each)
-	\item Not a linear function of pore size - radius increase by x, D increases by y
-	\item Larger influence on bigger molecules
-  \end{itemize}
-
-  \subsubsection{Experimental Measurements}
-
-  % For Greg
-
-  \subsection{Transport Mechanisms}
-
-  In order to truly understand the molecular origins of the macroscopic
-  diffusion coefficients in Section~\ref{section:D_macro}, we studied the
-  microscopic interactions between solutes and the membrane that lead to the
-  observed dwell time and hop distributions.
-  \begin{itemize}
-	\item We studied the radial distribution functions of solutes as a
-	function of distance from the pore center
-	\item We looked at hydrogen bonding patterns
-	\item Coordination numbers
-	\item Order parameters
-  \end{itemize}
-
-  The radial distribution function of each solute studied is shown in 
-  Figure TBD.
-
-  \subsubsection*{Transport of Water}
-
-  All water molecules exhibit hop diffusion.
-
-  Even in the center of the pore, where the density of water molecules is
-  highest, individual water molecules exhibit hop diffusion as they create a
-  tight hydrogen bond network.
-  %TODO: the following is a hypothesis
-  \begin{itemize}
-	\item Water sticks to pore walls
-	\item Dwell times are short
-	\item Water tumbles across pore for a while until it sticks again. 
-	\item Water gets caught in h-bonds with other water molecules away
-	from pore center.
-  \end{itemize}
-
-  In this confined environment, the diffusion constant is x times lower than
-  expected bulk diffusion coefficient of tip3p water.
-
-  %TODO: study diffusion mechanism of water
-
-  \subsubsection*{Transport of Alcohols}
-
-  The hydroxyl functional group of alcohol molecules is a hydrogen bond donor
-  and prefers to donate it's hydrogen to more strongly polarized carboxylate head
-  groups.
-
-  As alcohol groups increase in hydrophobic character, they are more inclined
-  to stick to the outside edges of the pore. 
-  \begin{itemize}
-	\item The alkane tails prefer to stay at the edges of the pore.
-	\item Radial distribution functions show peaks at pore edges, however
-	smaller alcohols have high densities near the pore center. 
-	\item They tend to get trapped between monomers and closer to 
-	the tail region. 
-	\item The entrapment is further stabilized by hydrogen bonds with
-	ether oxygens connecting the monomer's alkane tails to the head groups.
-	%TODO: quantify h-bonds with ether oxygens and carbonyl oxygens
-  \end{itemize}
-
-  The diffusion coefficient of simple alcohols increases as the length of 
-  the alkane chain increases.
-  \begin{itemize}
-	\item The dwell times increase as the oily tails become more
-	entrapped in monomer tails.
-  \end{itemize}
-
-  Ethylene glycol, a diol, has two hydrogen bond donor groups.
-  \begin{itemize}
-	\item Can hydrogen bond with same moeity.
-	\item Can hydrogen bond with different moeities in the same 
-	vicinity. 
-	\item Dwell times tend to be shorter. If one hydroxyl group is bound
-	with a hydrogen bond, the other unbound hydroxyl group may form a hydrogen bond
-	elsewhere and effectively pull the other bound hydroxyl group along with it. 
-  \end{itemize}
-
-  \subsubsection*{Transport of Acetone}
-
-  The carbonyl group of Acetone is a hydrogen bond acceptor and therefore only
-  form hydrogen bonds with water molecules in the pore.
-
-  The hydrophobic character of the two methyl groups on acetone causes the methyl
-  groups to gravitate towards the outside of the pore, while the carbonyl group
-  reaches towards the pore center in order to hydrogen bond with water molecules.
-  \begin{itemize}
-	\item Order parameter defined between vector along carbonyl and vector extending
-	from acetone COM to pore center is non-zero.
-  \end{itemize}
-
-  \subsubsection*{Transport of Acetic Acid}
-
-  Acetic acid, since we modeled it solely in its protonated state, has hydrogen
-  bond donor and acceptor groups.
-
-  \subsubsection*{Transport of Ions} % probably just sodium
-
-  Sodium ions also exhibit hop diffusion because polarized water and
-  carboxylate head groups both work to neutralize its charge.
-  \begin{itemize}
-	\item Ions get trapped in oxygen 'cages' composed of combinations
-	of water molecules, carboxylate head groups and ether oxygens connecting
-	the head groups to their tails.
-  	\item Interesting coordination number data
-	\item Dwell time proportional to surrounding charge within coordination shell
-  \end{itemize}
-
-  \subsubsection*{Remarks}
-
-  Overwhelming amount of water in 10 wt\% system makes hydrogen bonding
-  competitive between head groups and water.
-  %MRS: not sure what you mean above.
-
-  \subsection{Design Suggestions}
-
-  Water content affects pore size. Experiments to understand this could be useful.
-
-  Separate polar molecules by creating monomers with more hydrophilic head group components.
-  More incentive to dwell on walls.
-
-  Make ions move faster by placing charges in sterically inaccessible places.
+  %BJC: reduce this figure to solutes studied and put 3 bars for each solute: MD MSD, one-mode sfbm MSD, two-mode sfbm MSD
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{all_emsds.pdf}
+  \caption{}\label{fig:all_msds}
+  \end{figure}
 
@@
 
-  We have examined the transport characteristics of a series of small polar
-  molecules in our model of the H\textsubscript{II} phase formed by 
-  Na-GA3C11.
-
-  We calculated the macroscopic diffusion coefficients of each solute as 
-  approximated by a CTRW model and validated our estimates using experimental
-  DOSY NMR measurements.
-
-  We have studied the influence of water content on the diffusion coefficients.
-
-  We showed that hydrogen bonding between solutes and Na-GA3C11 monomers plays
-  a major role in mechanism by which molecules traverse the nanopores.
-
-  We can use this intuition in order to modify our monomers for a specific 
-  separation.
+  We have tested two different mathematical frameworks for describing solute
+  motion in an H\textsubscript{II} phase LLC membrane.
   \begin{itemize}
-	\item Increase number of h-bond sites to increase selectivity towards water 
-	over polar molecules
-	\item Also separate acetone (things with only h-bond accepting groups) in this way
+    \item Markov state modeling with predefined states gives a nice description
+    of transitions between observed states as well as the type of stochastic 
+    behavior shown in each state. However, it doesn't accurately portray correlated
+    time series behavior leading to overpredicted MSDs.
+    \item Subordinated fractional Brownian motion has a nice theoretical foundation
+    in the anomalous diffusion literature. A two mode model that describes dynamics
+    based on whether a solute is in or out of the pore region leads to MSDs fairly
+    consistent with MD simulated trajectories.
   \end{itemize}

### 2019-08-16 Ben_Manuscripts/stochastic_transport/Outline.tex
Outline updates and removing unnecessary files

@@
   %BJC: obviously this section will get beefed up
-  We need highly selective membranes in order to perform efficient separations.
+  We need highly selective membranes in order to perform efficient separations. \\
 
-  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.
+  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.\\
 
-  Lytropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
+  Lyotropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
   into mechanically strong membranes.
@@
   atomistic resolution so that we can intelligently design new membranes for 
-  solute-specific separations.
+  solute-specific separations.\\
 
-  In our previous work, we studied the transport of 20 small polar molecules
+  \noindent In our previous work, we studied the transport of 20 small polar molecules
   in an H\textsubscript{II} phase LLC membrane.
@@
   able to make well-converged predictions of macroscopic transport properties 
-  traditionally used to characterize membranes in the lab.
+  traditionally used to characterize membranes in the lab. \\
 
-  One can draw from a number of scientific field to model transport behavior as a
+  One can project long timescale solute behavior by modeling transport as a
   stochastic process.
   \begin{itemize}
-    \item In the simulation literature, most start with mean squared displacement (MSD)
-    \item Due to the time scales most people simulate, the MSD does not give a complete
-    picture of what happens long-term.
+    \item Various disciplines study this type of problem in a number of ways.
+    \item In the simulation literature, most start by measuring mean squared 
+    displacement (MSD), as we did previously.  % This doesn't quite fit the thesis
+    \item Due to the short time scales most people can feasibly simulate, the MSD 
+    does not give a complete picture of what happens long-term, other than hinting
+    at types of mechanisms that could lead to the curve's shape.
+    \item mean first passage time?
     \item Markov state models are popular with researchers of proteins which have 
     many dynamical states occurring over multiple time scales.
-    \item The anomalous diffusion literature 
-    \item The financial literature studies a wide range of time series behavior which 
-    may be particularly useful for describing short time scale dynamics.
+    \item The anomalous diffusion literature explains the shape of MSD curves based
+    on rigorous mathematical representations of transport mechanisms. This field is
+    heavily used in analysis of single particle tracking experiments.
+    \item Finally, the financial literature tackles similar problems from a more 
+    general time series perspective. Their primary focus is towards predictions of
+    stock market returns and volatility but their methods are widely applicable to
+    modeling time series that exhibit a range of behavior.
   \end{itemize}
 
-  % brief (1 paragraph) review of techniques for predicting long time scale behavior
-  The are numerous ways one can approach modeling transport behavior, withing varying
-  levels of complexity.
-  \begin{itemize}
-    \item Most
-
-    \item Mean first passage time?
-
-    \item Hidden markov models are useful for when states are known but one cannot
-  \end{itemize}
-  % Ornstein-Uhlenbeck (Gaussian + non-Gaussian)
-
-  Talk about finance, single particle tracking and other places this type of analysis
-  are used. Use word ubiquitous
-
-  In this work, we explore three approaches to model the long timescale behavior
+  In this work, we explore two approaches to model the long timescale behavior
   of the four solutes fasted moving solutes studied in our previous work.
@@
     \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
-  	\item Our first approach is based on the anomalous diffusion literature.
-  	\item The second approach uses Markov state models (MSMs) 
-  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
-  	learning algorithm which groups solute behavior into different dynamical states.
+  	\item Our first approach uses Markov state models (MSMs) 
+  	\item The second approach is based on the anomalous diffusion literature.
+%  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
+%  	learning algorithm which groups solute behavior into different dynamical states.
   	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
@@
 
-  We ran all MD simulations and energy minimizations using GROMACS 2018. We
+  We ran all MD simulations and energy minimizations using GROMACS 2018. We  % needs gromacs citations
   performed all post-simulation trajectory using python scripts which are available
-  online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
+  online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
 
@@
 
-  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
+  \noindent We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
   to collect ample data.
@@
     respectively.
+    \item We recorded frames every 0.5 ns
   \end{itemize}
@@
 
-  A Markov state model decomposes a time series into a set of discrete states
+  A Markov state model (MSM) decomposes a time series into a set of discrete states
   with transitions between states defined by a transition probability matrix, T,
@@
     \item In the context of molecular simulations, MSMs are frequently used
-    to study systems with slow dynamics, such as protein folding.~\cite{snow_how_2005,chodera_automatic_2007}
+    to study systems with slow dynamics, such as protein folding.~\cite{snow_how_2005,chodera_automatic_2007} % might move to intro
     \item Researchers typically aim to come up with a low dimensional 
@@
   	in dimensionality. 
+  	\item However, we will adopt the validation techniques used in the packages
+  	mentioned above.  
   	%BJC: not sure the best way to lay these out
@@
   	that may be relaxed in future work.
-  	\item However, we will adopt the validation techniques used in the packages
-  	mentioned above.  
   \end{itemize}
@@
     the transition dynamics is even more important.
-    %BJC: some of the transitions are pretty rare, so those emission distributions might be less reliable
-    \item The shape of the distributions are symmetric and heavy-tailed. 
+    \item This results in 64 distinct emission distributions. Some are far more
+    populated than others.
+% BJC: not sure if the emission distributions are reversible.
+i.e.
+if 1 --> 2 transition has same emission distribution as 2 --> 1.
+It might be required to be Markovian since transition matrix is symmetric.
+Not sure.
+    %\item The shape of the distributions are symmetric and heavy-tailed. 
   \end{itemize}
@@
   	emphasizes that these distributions are only an approximation.
-    \item We avoid unrealistic, enormous hops problem by truncating the tails
+    \item We avoid enormous and unrealistic hops problem by truncating the tails
     of the distribution. %BJC: can add some citations about truncated Levy distributions
@@
   \begin{itemize}
-    \item For each trajectory simulated, we chose an in initial state randomly from a 
+    \item For each trajectory simulated, we chose an initial state randomly from a 
     uniform distribution.
@@
   well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
-  metzler_anomalous_2014,neusius_subdiffusion_2009}
+  metzler_anomalous_2014,neusius_subdiffusion_2009}  % Note that this is different from the distribution of all increments (which is heavy-tailed)
   \begin{itemize}
@@
 
+  For the two mode model, we needed to define a probability transition matrix 
+  describing transitions between the tail and pore region.
+
 %  We generated distributions of parameters for the dwell time and hop length
@@
 	distributions.
-	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
-	the last data point so that the total time exactly equaled 5 $\mu$s. 
+	\item We propagated each trajectory until the total time equaled or exceeded 5 $\mu$s, 
+	then truncated the last data point so that the total time exactly equaled 5 $\mu$s. 
     \item Valid comparisons are only possible between fixed length sFBM simulations. The
@@
 
-%  \subsubsection*{Coordination number}
-
-%  We quantified the coordination of solutes with surrounding molecules.
-%  \begin{itemize}
-%  	\item For each frame, we counted the identities and number of
-%  	coordinated molecules to a given solute based on a distance cut-off. 
-%	\item We found that this approach is more useful than calculating the
-%	3D spherical radial distribution function because it gives detailed
-%	frame-by-frame information rather than an average. 
-%  \end{itemize}
-
+  % BJC: can ignore this section for now. 
   \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}  %BJC: potentially a separate paper
@@
     a priori.
+    \item One can partially overcome this by testing a range of numbers of 
+    hidden states and determining which is the best representation of their
+    data.
   \end{itemize}
@@
     each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
+    \item Once the model has converged only a finite number of states will have significant
+    sampling.
   \end{itemize}
@@
 
-  Solute motion is influenced by the same three trapping mechanisms observed in our
-  previous works.
+  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
+  previous work.
   \begin{itemize} 
@@
   \begin{figure}[!h]
-  \includegraphics[width=\textwidth]{MET_msd.pdf}
+  \centering
+  \includegraphics[width=0.5\textwidth]{MET_msd.pdf}
   \caption{}\label{fig:msd_MET}
@@
 
-  Anti-correlation between hops may be responsible for subdiffusive behavior.
+  \noindent Anti-correlation between hops may be responsible for subdiffusive behavior.
   \begin{itemize}
@@
     \item Therefore we did not do this and attempted to fit a different model. 
-    %BJC: we could add some artificial correlation to test the anti-correlation hypothesis
+    %BJC: we could add some artificial correlation to prove the anti-correlation hypothesis
   \end{itemize}
@@
 
-  Using the techniques from Section~\ref{section:model_sFBM}, we extracted values 
+  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
   of $\sigma$, $\alpha$ and $H$ for each solute for the 1 and 2 mode model 
@@
   \begin{itemize}
-    \item In most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the
-    simulated MSD values presented in Table~\ref{table:simulations}. 
+    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
+    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values . 
   	\item Higher values of $\sigma$ indicate larger average hop lengths.
@@
   % BJC: obviously still needs 2 mode data
+  % BJC: this is 1 microsecond data
   \begin{table}[h]
@@
 	\item We simulated 10000 sFBM trajectories of the same length as our MD
-	simulations, as described in Section~\ref{section:model_sFBM} of the Methods.
+	simulations, as described in Section~\ref{method:model_sFBM} of the Methods.
 	\item The final MSDs of the sFBM trajectories are compared to those 

### 2019-08-20 Ben_Manuscripts/stochastic_transport/Outline.tex
comments on outline.

@@
 
+%MRS: better to have the first outline shorter to iterate more quickly!
+
+%MRS: better to have a title that described a finding, rather than the
+%approach used.  But we may need to wait a bit further until we can decide on a finding.
+%MRS: also 'stochastic modeling' is pretty vague.  should be more precise. 
 \title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+%MRS: we should discuss whether Chris Calderon would be on this one.  I would guess no, but I don't know for sure. 
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   % BJC: Maybe it's just a combination of both.
+
+  % MRS: They way to think about it, I think, is that the simplest
+  % assumption is the the transport mechanism is simple diffusion;
+  % uncorrelated random jumps due to molecular collisions. If you make
+  % that assumption, you get MSD linear in time.  So that's IS a
+  % stochastic process, but not a very complex one. To make long
+  % timescale predictions, we need to increase the detail.  Is that
+  % what you are referring to? Not sure if I answered the question . . .
+
   Unfortunately, the timescales that we can simulate with MD are insufficient to be
@@
   stochastic process.
+  %MRS: as above, simple diffusion is stochastic, just not very complex.  So we want to add appropriate complexity.
   \begin{itemize}
+    %MRS: best talk about these mechanisms in terms of the
+    %mathematical models they capture.  But I don't know that it's
+    %necessary to review all of them.
+
+    %It may be a better approach to start from the features of the
+    %problem (i.e. certain mechanisms) and choose the model (of the
+    %existing choices) that is appropriate for those mechanisms.
+    %I.e. diagnose first, then choose, rather than just applying a
+    %list of models useful in other field's timeseries. Let me know if that makes sense;
+    %I think how the methods applied are selected is a key to solve the problem.
+
     \item Various disciplines study this type of problem in a number of ways.
@@
     at types of mechanisms that could lead to the curve's shape.
+    %MRS: I'd say that MSD is too simple compared to what is going on mechanistically, but it's fundamentally the same idea.  
     \item mean first passage time?
@@
   performed all post-simulation trajectory using python scripts which are available
+  %MRS: eventually want to say what scripts were used to do what, but that is not at the outline stage!
   online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
@@
     as much structural space as possible.  %BJC: better term than structural space?
+    %MRS: something simpler like ``sample the accessible mechanisms with representative probability''?
   \end{itemize}
@@
     have a relatively diverse set of chemical functionality.   
+    %MRS: do the solutes also have some diversity of mechanisms (that were observed previously?)
     \item For each solute we created a separate system and to each system we
@@
 
+  %MRS: probably write it as a 2x4 table.
   In this work, we define a total of 8 discrete states based on the 3 trapping
@@
 
+  %MRS: this below sort of goes beyond standard use of MSM's though, right? where everything is usually constant-rate expoential processes? Should be explicitly mentioned.
   \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
@@
     \begin{equation}
-    p_{\alpha, \beta}(k;\mu,\sigma) = exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
+    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
     \end{equation}
@@
     \item We will discuss the implications of each.  
+    %MRS: does the process described above include the motion within the state? That is something I feel that the
+    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
   \end{itemize}
@@
 
+  %MRS: you intend this to be a separate model than the above?  If so, make clearer.
   \subsection{Modeling subdiffusion}\label{method:model_sFBM}
@@
   \begin{itemize}
+  %MRS: you would probably want to be clear what the mechanistic reasons for for anomalous diffusion: 
+  %want to talk about why, given the mechanisms you would consider. 
   	\item During an anomalous diffusion process, the mean squared displacement (MSD)
@@
   \begin{itemize}
+    %MRS: describe the physical situations in which one would want to choose each of these ways of calculating the MSD.
 	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
@@
   \end{itemize}
+  %MRS: talk about which of these should apply given the data mechanistically, as well as fit.
 
   % BJC: Should this be in the results? Lots of figures to show in support of the claims below
+  %MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
+
   \noindent We believe that solutes in the system studied here exhibit subordinated 
@@
   pore versus in the tail region.
+
+  %MRS: could present the two models sequentiually.  Talk about one COULD have multiple modes, then in results present 1, then 2.
+
   \begin{itemize}
@@
   \begin{itemize}
+    %MRS: probably option 1.
     \item 2 options for a figure:
@@
 
+  %MRS: I'm not sure where the below is different from what was found in the previous study (i.e MSD's).
   \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
@@
   % BJC: worth proving these are non-Gaussian? One might argue that they look Gaussian but they are not at all.
+  % MRS: there are some simple statistical tests for Gaussianness you can use.  Also might br good to put the 
+  % parameters with the plots, as it's hard to tell how different they may or may not be. 
   \begin{figure}[!h]
@@
   % BJC: or could say that whenever we say simulations, we mean stochastic simulations unless it is specified as a molecular dynamics simulation.
+  % MRS: could say timeseries simulation?  MD is stochastic as well.
   Simulating solute trajectories (see Section~\ref{method:MSMs}) by drawing independent  
@@
   \end{itemize}
-
+  %MRS: so, is there a way we should have been able to tell beforrehand that this approach didn't work that we an explain?
+  %or can we show we needed to do this to get the results?
   \begin{figure}[!h]

### 2019-08-22 Ben_Manuscripts/stochastic_transport/Outline.tex
solved atom naming bug
Responses to some comments

@@
 %MRS: we should discuss whether Chris Calderon would be on this one.  I would guess no, but I don't know for sure. 
+%BJC1: Yea maybe Chris as an acknowledgement on this one. He didn't directly contribute anything other than pointing
+%me towards Greg Morrin who pointed me towards useful anomalous diffusion literature.
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   % what you are referring to? Not sure if I answered the question . . . 
+  % BJC1: Yea, I see what you're saying. Just not sure what else the long
+  % timescale will tell us that we can't learn from short ones. Probably 
+  % better to talk about this in person.
 
@@
 
-  One can project long timescale solute behavior by modeling transport as a
+  We can use the observed mechanisms in order to choose a stochastic model of
+  sufficient complexity One can project long timescale solute behavior by modeling transport as a
   stochastic process.
@@
   %MRS: eventually want to say what scripts were used to do what, but that is not at the outline stage!
+  %BJC1: I usually put a table like that in the SI. Is that sufficient?
   online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
@@
     significantly faster than in the 5 wt \% system studied previously.
-    \item Appropriate stochastic modeling requires that solutes explore 
-    as much structural space as possible.  %BJC: better term than structural space?
-    %MRS: something simpler like ``sample the accessible mechanisms with representative probability''?
+    \item Appropriate stochastic modeling requires that solutes sample the 
+    accessible mechanisms with representative probability.  %BJC1: incorporated suggested phrasing
   \end{itemize}
@@
     %MRS: do the solutes also have some diversity of mechanisms (that were observed previously?)
+    %BJC1: Yes. Need to put following into words
+    %BJC1: Ranking of time spent in pore region: AcOH > EG > URE > MeOH  (spans 4th most to 3rd least)
+    %BJC1: All have high hop frequency which is consistent with fast motion
+    %BJC1: Hbonding: Urea barely hbonds. AcOH and EG hbond a lot. AcOH has highest hbond lifetime of all 20 solutes. MeOH on par with all other simple alcohols
+    %BJC1: Sodium Association: Urea coordinates with sodium the most of all 20 solutes. AcOH, EG, MeOH spread out of rest of range. Lifetime similar 
     \item For each solute we created a separate system and to each system we
@@
 
-  %MRS: this below sort of goes beyond standard use of MSM's though, right? where everything is usually constant-rate expoential processes? Should be explicitly mentioned.
+  % MRS: this below sort of goes beyond standard use of MSM's though, right? where everything is 
+  % usually constant-rate expoential processes? Should be explicitly mentioned.N
+  %BJC1: yes
   \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
@@
     \item We avoid enormous and unrealistic hops problem by truncating the tails
-    of the distribution. %BJC: can add some citations about truncated Levy distributions
+    of the distribution. %BJC: can add some citations about truncated Levy distributions which are used frequently in modeling
     \item Since solutes in our system cannot hop further than the length of our 
@@
   %MRS: you intend this to be a separate model than the above?  If so, make clearer.
-  \subsection{Modeling subdiffusion}\label{method:model_sFBM}
+  %BJC1: renamed, is that what you meant?
+  \subsection{The Anomalous Diffusion Model}\label{method:model_sFBM}
 
@@
   %want to talk about why, given the mechanisms you would consider. 
+  %BJC1: could go through flow chart
   	\item During an anomalous diffusion process, the mean squared displacement (MSD)
@@
     %MRS: describe the physical situations in which one would want to choose each of these ways of calculating the MSD.
+    %BJC1: For determining ergodicity. Ensemble for determining anomalous exponent. Not sure I'll use ensemble MSD
 	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
@@
   %MRS: talk about which of these should apply given the data mechanistically, as well as fit.
+  %BJC1: I believe that's what I try to do in the paragraph below. I can be a little more explicit
 
@@
   %or can we show we needed to do this to get the results?
+  %BJC1: could just show autocorrelation function of all increments, which has negative dip at k=1 
   \begin{figure}[!h]

### 2019-08-26 Ben_Manuscripts/stochastic_transport/Outline.tex
Added back dummy energy minimization

@@
 %MRS: better to have the first outline shorter to iterate more quickly!
+%BJC1: right, this one has been in the works for a while now. Wrote the anomalous diffusion methods a long time ago
 
@@
   \begin{itemize}
-    \item In general, we observed subdiffusive transport behavior characterized 
-    by intermittent hops separated by periods of entrapment.
+    \item In general, we observed subdiffusive transport behavior characterized by 
+    intermittent hops separated by periods of entrapment.
     \item We identified three mechanisms responsible for the solute trapping behavior:
@@
   \end{itemize}
+
+  Unfortunately, the timescales that we can simulate with MD are insufficient to be
+  able to make well-converged predictions of macroscopic transport properties 
+  traditionally used to characterize membranes in the lab. \\
+  \begin{itemize}
+    \item However, if we use descriptive stochastic models that can capture solute
+    dynamics, then we could project long timescale behavior in addition to gaining
+    a deeper understanding of solute behavior on short timescales.
+  \end{itemize}
+
+  \noindent Researchers have developed a rigorous theoretical foundation for describing
+  the motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
+  \begin{itemize}
+    \item The tools introduced by fractional calculus are instrumental to this theory. 
+    \item They allow us to generalize the normally linear diffusion equation using fractional
+    derivative orders, providing descriptions of a much more diverse set of behavior. % diverging from the relatively simple Brownian model.
+%    \item They facilitate proof of the relationship between the observed growth of a
+%    particle's mean squared displacement and underlying dwell times 
+%    \item In the absence of an external potential or complicated boundary conditions, 
+%    one can define random walk based on independent hop length and dwell time 
+%    distributions and arrive at any type of diffusive behavior. 
+  \end{itemize}
+
+  % BJC1: moved from methods
+  \noindent Three well-known classes of behavior leading to anomalous subdiffusion are 
+  continuous time random walks (CTRW), fractional Brownian motion
+  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
+  \begin{itemize}
+    \item A CTRW is characterized by a distribution of hop lengths and 
+    dwell times, where each each hop is characterized by independent random draws from 
+    each distribution.\cite{montroll_random_1965,morrin_three_2018}
+    \item FBM is common in crowded, viscoelastic environments where each jump comes 
+    from a Gaussian distribution but is anti-correlated to its previous 
+    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
+    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
+    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
+    \item The processes described above can happen alone or in combination. 
+    \item Meroz and Sokolov suggested a decision tree for determining which subdiffusive
+    mechanisms apply to a system, adapted in Figure X. 
+    \item Of course, more complicated variations of these models can arise which we 
+    will incorporate as needed.	  % BJC1: e.g. fractional levy motion or langevin with levy noise
+  \end{itemize}
+
+  % BJC1: Flow chart here
+
+  While elegant, pure anomalous diffusion theory may in some cases give only a qualitative
+  understanding of transport mechanisms.
+  \begin{itemize}
+    \item Complex temporal relationships in between hops may have a significant effect on MSD
+    \item Inhomogeneity of a medium or multiple types of interactions may lead to a number of
+    distinct diffusive regimes. 
+    \item In this case, a state based model may be useful. 
+  \end{itemize}
+
+  We can use the observations of transport from our previous work in order to create 
+  state-based models.
+  \begin{itemize}
+  	\item We know that dynamics differ between solutes moving inside the pores and in the tails.
+  	\item We can fit the above models to our data as a function of location.
+  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
+  	methods of Markov state models.
+  \end{itemize}
+
+  Markov state models blah blah blah.
+  \begin{itemize}
+    \item Markov state models are popular with researchers of proteins which have 
+    many dynamical states occurring over multiple time scales.
+  \end{itemize}
+
+  We will extend the Markov state models framework to include dynamics between jumps.
 
@@
   % better to talk about this in person.
-
-  Unfortunately, the timescales that we can simulate with MD are insufficient to be
-  able to make well-converged predictions of macroscopic transport properties 
-  traditionally used to characterize membranes in the lab. \\
 
@@
 
+  % BJC: quote from anomalous diffusion book:
+  % "While the continuous time random walk model for Levy flights ... is a
+  % conventient description, in all other cases the fraction Fokker-Planck or,
+  % equivalently, the Langevin equation with white Levy stable noise are the 
+  % description of choice" -- pretty sure this is exactly what I'm suggesting above.
+
   L\'evy stable distributions often have heavy tails and an undefined variance 
@@
 
-  \noindent Three common mathematical models for modeling anomalous subdiffusion
-  processes include continuous time random walks (CTRW), fractional Brownian motion
-  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
-  \begin{itemize}
-    \item FBM is common in crowded, viscoelastic environments where each step comes 
-    from a Gaussian distribution but is anti-correlated to its previous 
-    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
-    \item A CTRW is characterized by a distribution of hop lengths and 
-    dwell times, where each each step is characterized by independent random draws from 
-    each distribution.\cite{montroll_random_1965,morrin_three_2018}
-    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
-    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
-    \item The processes described above can happen alone or in combination.  	
-  \end{itemize}
+  % BJC1: moved this to intro
+%  \noindent Three common mathematical models for modeling anomalous subdiffusion
+%  processes include continuous time random walks (CTRW), fractional Brownian motion
+%  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
+%  \begin{itemize}
+%    \item FBM is common in crowded, viscoelastic environments where each step comes 
+%    from a Gaussian distribution but is anti-correlated to its previous 
+%    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
+%    \item A CTRW is characterized by a distribution of hop lengths and 
+%    dwell times, where each each step is characterized by independent random draws from 
+%    each distribution.\cite{montroll_random_1965,morrin_three_2018}
+%    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
+%    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
+%    \item The processes described above can happen alone or in combination.  	
+%  \end{itemize}
   %MRS: talk about which of these should apply given the data mechanistically, as well as fit.
@@
   %MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
-
   \noindent We believe that solutes in the system studied here exhibit subordinated 

### 2019-08-27 Ben_Manuscripts/stochastic_transport/Outline.tex
Outline updates

@@
   \begin{itemize}
-    \item However, if we use descriptive stochastic models that can capture solute
+    \item However, if we use descriptive stochastic models that sufficiently capture solute
     dynamics, then we could project long timescale behavior in addition to gaining
@@
     \item The tools introduced by fractional calculus are instrumental to this theory. 
-    \item They allow us to generalize the normally linear diffusion equation using fractional
-    derivative orders, providing descriptions of a much more diverse set of behavior. % diverging from the relatively simple Brownian model.
+    \item They allow us to generalize the normally linear diffusion equation to fractional
+    derivative orders, providing descriptions of a much more diverse set of behavior. \cite{klages_anomalous_2008} % diverging from the relatively simple Brownian model.
 %    \item They facilitate proof of the relationship between the observed growth of a
@@
   \begin{itemize}
+    \item The theory is frequently used to describe single particle trajectories
     \item A CTRW is characterized by a distribution of hop lengths and 
@@
     mechanisms apply to a system, adapted in Figure X. 
-    \item Of course, more complicated variations of these models can arise which we 
+    \item Of course, more complicated variations on these models can arise which we 
     will incorporate as needed.	  % BJC1: e.g. fractional levy motion or langevin with levy noise
@@
   \begin{itemize}
-    \item Complex temporal relationships in between hops may have a significant effect on MSD
+    \item Complex temporal relationships in between hops may have a significant effect on the average MSD
     \item Inhomogeneity of a medium or multiple types of interactions may lead to a number of
@@
 
-  We can use the observations of transport from our previous work in order to create 
+  \noindent We can use the observations of transport from our previous work in order to create 
   state-based models.
   \begin{itemize}
-  	\item We know that dynamics differ between solutes moving inside the pores and in the tails.
-  	\item We can fit the above models to our data as a function of location.
+  	\item We know that dynamics differ between solutes moving inside the pores and 
+  	in the tails.
+  	\item We can use the anomalous diffusion approach to model to our data as a 
+  	function of radial distance from the closest pore center.
   	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
-  	methods of Markov state models.
+  	methods of Markov state modeling.
   \end{itemize}
 
-  Markov state models blah blah blah.
+  % moved parts of method to here.
+  Markov state models (MSMs) are a popular class of models used to project long timescale
+  behavior of molecules based on molecular simulation trajectories by identifying
+  different dynamical modes and quantifying the rates of transitions between them.
   \begin{itemize}
-    \item Markov state models are popular with researchers of proteins which have 
-    many dynamical states occurring over multiple time scales.
+    \item MSMs are frequently used to study systems with slow dynamics, such as protein 
+    folding.~\cite{snow_how_2005,chodera_automatic_2007}
+    \item Researchers typically aim to come up with a low dimensional 
+    representation of the system based on features which preserve the process
+    kinetics.
+    \item This still often results in thousands of distinct states. 
   \end{itemize}
 
-  We will extend the Markov state models framework to include dynamics between jumps.
+  In this work we attempt to model the long timescale behavior of the four 
+  fastest moving solutes studied in our previous work.
+  \begin{itemize}
+    \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
+    \item In addition to moving quickly, these solutes have a range of chemical
+    functionality and experience each of the three trapping mechanisms to different
+    degrees.
+    \item It is our goal to reproduce the MSDs exhibited by each solute on MD timescales
+    and then to project the long-term dynamics of each solute. 
+    \item We explore two modeling approaches
+%  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
+%  	learning algorithm which groups solute behavior into different dynamical states.
+  	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
+  	% require anything different in systems with more complex geometries (i.e. QI)
+  \end{itemize}
+
+  Our first approach is based on the anomalous diffusion literature, applying the 
+  mathematical formalism describing subdiffusive transport to observed solute 
+  trajectories.
+  \begin{itemize}
+    \item We determine the most likely subdiffusive mechanisms at play using the 
+    flow chart in figure X. 
+    \item We then fit anomalous diffusion models in two ways: First, based on a
+    single set of parameters. Second, we use a two-state approach incorporating
+    two sets of parameters based on a solute's radial distance from the pore center. 
+  \end{itemize}
+
+  The second approach adapts the MSM framework to a relatively small set of known 
+  states based on the three observed solute trapping mechanisms.
+  \begin{itemize}
+    \item We extend the framework to include dynamics between jumps. 
+    \item That is we incorporate the magnitude and temporal dependence of the 
+    time series fluctuations between each transition to a different state. 
+    \item Temporal dependence has a significant influence on mean squared displacement.
+  \end{itemize}
 
@@
 
-  We can use the observed mechanisms in order to choose a stochastic model of
-  sufficient complexity One can project long timescale solute behavior by modeling transport as a
-  stochastic process.
-  %MRS: as above, simple diffusion is stochastic, just not very complex.  So we want to add appropriate complexity.
-  \begin{itemize}
-    %MRS: best talk about these mechanisms in terms of the
-    %mathematical models they capture.  But I don't know that it's
-    %necessary to review all of them.
-
-    %It may be a better approach to start from the features of the
-    %problem (i.e. certain mechanisms) and choose the model (of the
-    %existing choices) that is appropriate for those mechanisms.
-    %I.e. diagnose first, then choose, rather than just applying a
-    %list of models useful in other field's timeseries. Let me know if that makes sense;
-    %I think how the methods applied are selected is a key to solve the problem.
-
-    \item Various disciplines study this type of problem in a number of ways.
-    \item In the simulation literature, most start by measuring mean squared 
-    displacement (MSD), as we did previously.  % This doesn't quite fit the thesis
-    \item Due to the short time scales most people can feasibly simulate, the MSD 
-    does not give a complete picture of what happens long-term, other than hinting
-    at types of mechanisms that could lead to the curve's shape.
-    %MRS: I'd say that MSD is too simple compared to what is going on mechanistically, but it's fundamentally the same idea.  
-    \item mean first passage time?
-    \item Markov state models are popular with researchers of proteins which have 
-    many dynamical states occurring over multiple time scales.
-    \item The anomalous diffusion literature explains the shape of MSD curves based
-    on rigorous mathematical representations of transport mechanisms. This field is
-    heavily used in analysis of single particle tracking experiments.
-    \item Finally, the financial literature tackles similar problems from a more 
-    general time series perspective. Their primary focus is towards predictions of
-    stock market returns and volatility but their methods are widely applicable to
-    modeling time series that exhibit a range of behavior.
-  \end{itemize}
-
-  In this work, we explore two approaches to model the long timescale behavior
-  of the four solutes fasted moving solutes studied in our previous work.
-  \begin{itemize}
-    \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
-  	\item Our first approach uses Markov state models (MSMs) 
-  	\item The second approach is based on the anomalous diffusion literature.
-%  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
-%  	learning algorithm which groups solute behavior into different dynamical states.
-  	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
-  	% require anything different in systems with more complex geometries (i.e. QI)
-  \end{itemize}
+%  We can use the observed mechanisms in order to choose a stochastic model of
+%  sufficient complexity One can project long timescale solute behavior by modeling transport as a
+%  stochastic process.
+%  %MRS: as above, simple diffusion is stochastic, just not very complex.  So we want to add appropriate complexity.
+%  \begin{itemize}
+%    %MRS: best talk about these mechanisms in terms of the
+%    %mathematical models they capture.  But I don't know that it's
+%    %necessary to review all of them.  
+%  
+%    %It may be a better approach to start from the features of the
+%    %problem (i.e. certain mechanisms) and choose the model (of the
+%    %existing choices) that is appropriate for those mechanisms.
+%    %I.e. diagnose first, then choose, rather than just applying a
+%    %list of models useful in other field's timeseries. Let me know if that makes sense;
+%    %I think how the methods applied are selected is a key to solve the problem.
+%
+%    \item Various disciplines study this type of problem in a number of ways.
+%    \item In the simulation literature, most start by measuring mean squared 
+%    displacement (MSD), as we did previously.  % This doesn't quite fit the thesis
+%    \item Due to the short time scales most people can feasibly simulate, the MSD 
+%    does not give a complete picture of what happens long-term, other than hinting
+%    at types of mechanisms that could lead to the curve's shape.
+%    %MRS: I'd say that MSD is too simple compared to what is going on mechanistically, but it's fundamentally the same idea.  
+%    \item mean first passage time?
+%    \item Markov state models are popular with researchers of proteins which have 
+%    many dynamical states occurring over multiple time scales.
+%    \item The anomalous diffusion literature explains the shape of MSD curves based
+%    on rigorous mathematical representations of transport mechanisms. This field is
+%    heavily used in analysis of single particle tracking experiments.
+%    \item Finally, the financial literature tackles similar problems from a more 
+%    general time series perspective. Their primary focus is towards predictions of
+%    stock market returns and volatility but their methods are widely applicable to
+%    modeling time series that exhibit a range of behavior.
+%  \end{itemize}
 
@@
   atomistic molecular model of four pores in a monoclinic unit cell with 
-  10 \% water by weight. 
+  10 \% water by weight. (See Figure tbd)
   \begin{itemize}
@@
 
-  \subsection{Markov State Models}\label{method:MSMs}  % BJC: this section first in hopes that sfbm works better
-
-  A Markov state model (MSM) decomposes a time series into a set of discrete states
-  with transitions between states defined by a transition probability matrix, T,
-  which describes the conditional probability of jumping to a specific 
-  state given the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
-  \begin{itemize}
-    \item In the context of molecular simulations, MSMs are frequently used
-    to study systems with slow dynamics, such as protein folding.~\cite{snow_how_2005,chodera_automatic_2007} % might move to intro
-    \item Researchers typically aim to come up with a low dimensional 
-    representation of the system based on features which preserve the process
-    kinetics. This facilitates the identification of discrete states from
-    which T is generated.
-    \item Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011}
-    and pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable 
-    of featurization and dimensional reduction.
-  \end{itemize}
-
-  %MRS: probably write it as a 2x4 table.
-  In this work, we define a total of 8 discrete states based on the 3 trapping
-  mechanisms observed in our previous work. 
-  \begin{itemize}
-  	\item Therefore, there is no need to subject our trajectories to any reduction
-  	in dimensionality. 
-  	\item However, we will adopt the validation techniques used in the packages
-  	mentioned above.  
-  	%BJC: not sure the best way to lay these out
-  	\item The states we've chosen include all combinations of trapping mechanisms 
-  	in the pore and out of the pore:
-  	\begin{enumerate}
-  	  \item Trapped in tails
-  	  \item Trapped in tails and hydrogen bonding
-  	  \item Trapped in tails and associated with sodium
-  	  \item Trapped in tails, hydrogen bonding and associated
-  	  \item In pores
-  	  \item In pores and hydrogen bonding
-  	  \item In pores and associated with sodium
-  	  \item In pores, hydrogen bonding and associated
-  	\end{enumerate}
-  	\item These choices assume that there are no significant kinetic effects resulting
-  	from solute conformational changes or pore size fluctuations, an assumption 
-  	that may be relaxed in future work.
-  \end{itemize}
-
-  % BJC: does it make sense to use Dirichlet Process as a conjugate prior for
-  % getting error on transition matrix?
-
-  \noindent We constructed a state transition probability matrix based on observed solute
-  trajectories.
-  \begin{itemize}
-    \item Using methods described in our previous work, we determined 	
-    which, if any, trapping mechanisms affected the solute at each time step, and
-    assigned the observation to a specific state according to the definitions 
-    above.~\cite{coscia_chemically_2019}
-    \item Based on the current and previous state observation, we incremented the
-    appropriate entry of an $n x n$ count matrix by 1, where $n$ is the number of states.
-    \item For example, if we observed state 1 followed by a transition to state 3,
-    we increment the $(1, 3)$ entry of the count matrix by 1.
-    \item We generate the transition probability matrix from the count matrix by 
-    normalizing the entries in each row so that they summed to unity.
-  \end{itemize}
-
-  \noindent We recorded the $z$-direction displacement at each time step in order to construct
-  individual emission distributions for each state and transition between states.
-  \begin{itemize}
-    \item While the dynamics of the states themselves are important, the 
-    majority of observations involve transitions between states, so properly modeling
-    the transition dynamics is even more important.
-    \item This results in 64 distinct emission distributions. Some are far more
-    populated than others.
-% BJC: not sure if the emission distributions are reversible.
-i.e.
-if 1 --> 2 transition has same emission distribution as 2 --> 1.
-It might be required to be Markovian since transition matrix is symmetric.
-Not sure.
-    %\item The shape of the distributions are symmetric and heavy-tailed. 
-  \end{itemize}
-
-  % MRS: this below sort of goes beyond standard use of MSM's though, right? where everything is 
-  % usually constant-rate expoential processes? Should be explicitly mentioned.N
-  %BJC1: yes
-  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
-  \begin{itemize}
-    \item For independent and identically distributed (iid) random variables, the 
-    generalized central limit theorem guarantees convergence of the associated 
-    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
-    % BJC: ``For sums of independent, iid random variables with proper normalization to the
-%    sample size, the generalized central limit theorem guarantees the convergence of
-%    the associated PDF to a L\'evy stable PDF even though the variance of these random
-%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
-    \item The characteristic equation describing the Fourier transform of a L\'evy 
-    stable PDF is given below:
-    \begin{equation}
-    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
-    \end{equation}
-    \item Where $\omega$ is defined with something that is complicated to format and can be 
-    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
-    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
-    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
-    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
-    functions, is the Gaussian PDF ($\alpha$ = 2).
-    \item The more general family of L\'evy stable distributions allows
-    greater flexibility in defining the observed emission distribution PDFs.
-    \item In the case that the empirical emission distributions are iid, sequential draws
-    from a L\'evy stable PDF defines a L\'evy process. 
-    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
-    probability distributions if we instead consider the dynamics to be governed by a
-    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
-    \item OU processes contain temporal dependence but the marginal observation distributions
-    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
-    \item We will discuss the implications of each.  
-    %MRS: does the process described above include the motion within the state? That is something I feel that the
-    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
-  \end{itemize}
-
-  % BJC: quote from anomalous diffusion book:
-  % "While the continuous time random walk model for Levy flights ... is a
-  % conventient description, in all other cases the fraction Fokker-Planck or,
-  % equivalently, the Langevin equation with white Levy stable noise are the 
-  % description of choice" -- pretty sure this is exactly what I'm suggesting above.
-
-  L\'evy stable distributions often have heavy tails and an undefined variance 
-  which can give rise to arbitrarily long particle displacements.
-  \begin{itemize}
-  	\item We do not observe hops longer than x nm in our simulations which 
-  	emphasizes that these distributions are only an approximation.
-    \item We avoid enormous and unrealistic hops problem by truncating the tails
-    of the distribution. %BJC: can add some citations about truncated Levy distributions which are used frequently in modeling
-    \item Since solutes in our system cannot hop further than the length of our 
-    simulation unit cell, we truncate the tails of the distribution at this
-    magnitude.
-    % BJC: Is this actually the right way to do this? I am looking at unwrapped coordinates,
-    % so theoretically a particle can move as far as it wants between frames.
-    % BJC: The cut-off choice is pretty important and has a significant effect on MSD. 
-    % For example, if I truncate at the unit cell length I reproducably get a final MSD of ~ 66 nm^2 (1000 ns stochastic simulation)
-    % If I truncate the tails at double the unit cell length, I get a final MSD of ~107 nm^2
-    % The uncertainty also increases (since variance diverges for these distributions)
-    % So maybe it makes the most sense to truncate based on largest observed hops.
-  \end{itemize}
-
-  We simulated realizations of the stochastic process using the probability transition
-  matrix and emission distributions.
-  \begin{itemize}
-    \item For each trajectory simulated, we chose an initial state randomly from a 
-    uniform distribution.
-%BJC: could construct initial distribution but I'm not sure how reliable that is based on 24 solutes that are started in the pore center.
-(need to chop off beginning 5 ns or so to get rid of that initial dependence)
-    \item We randomly drew subsequent state transitions and corresponding emissions 
-    from the rows of the probability transition matrix and the appropriate emission
-    distribution respectively.
-  \end{itemize}
-
-  %BJC: need to add some validation of Markovian behavior and time step choice.
-
-  %MRS: you intend this to be a separate model than the above?  If so, make clearer.
-  %BJC1: renamed, is that what you meant?
+  % MRS: you intend this to be a separate model than the above?  If so, make clearer.
+  % BJC1: renamed, is that what you meant?
   \subsection{The Anomalous Diffusion Model}\label{method:model_sFBM}
@@
   	\item During an anomalous diffusion process, the mean squared displacement (MSD)
-  	does not grow linearly with time, rather it is of the form:
+  	does not grow linearly with time, rather it follows a power law of the form:
 	\begin{equation} 
@@
   % BJC: Should this be in the results? Lots of figures to show in support of the claims below
-  %MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
+  % MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
+  % BJC1: modified this paragraph to parallel the flow chart. I'm still not sure the
+  % best place for this. It seems like it belongs in the discussion, but I need to 
+  % justify the choice in model so I can write the methods about the chosen models
   \noindent We believe that solutes in the system studied here exhibit subordinated 
@@
   \begin{itemize}
-  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
-  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}  % BJC: need a figure to show this
-  	\item We also observe non-stationary $z$-coordinate traces of each solute's
+    \item Working down the flow chart...
+  	\item We observe non-stationary $z$-coordinate traces of each solute's
   	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
-  	\item For a pure CTRW, the time-averaged MSD should be linear.
-  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
-  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
-  	information), which suggests that there is another underlying subdiffusive mechanism.
-  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
+  	\item Combined with the observation that the ensemble-averaged MSD differs
+  	from the time-averaged MSD, we have evidence of non-ergodicity in this system, 
+  	a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}  % BJC: need a figure to show this
+% BJC1: following two points are weak. Linearity of CTRW doesn't necessarily hold up on short time scales.
+%  	\item For a pure CTRW, the time-averaged MSD should be linear.
+%  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
+%  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
+%  	information), which suggests that there is another underlying subdiffusive mechanism.
+	\item The process is likely subordinated to another process because the hop 
+	lengths recorded after each dwell period are anti-correlated.
+    % BJC1: need to eliminate RWF. I think a geometric argument should be convincing enough. Our
+    % system doesn't have a fractal-like structure. Monomer positions fluctuate enough that
+    % solutes can access any part of the membrane over time.
   	\item Given the viscoelastic nature of the monomers in our system, we believe
   	the hop lengths can be modeled with FBM. 
+  	% BJC1 : probably won't need this equation. It's really just to validate my sfbm
+  	% simulation procedure. Could go in supporting information with a plot showing that
+  	% my sims fit to t^alpha*beta
  	\item For subordinated FBM, it can be shown that
@@
   \begin{itemize}
-	\item We used the \texttt{ruptures} python package in order to identify
+	\item We used the \texttt{ruptures} python package in order to automatically identify
 	changepoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting
@@
 
+  % BJC1: not sure about this anymore. Might eventually change to Levy. But in the 
+  % interest of simplicity, maybe leave it at Gaussian.
   For solutes in our system, the distribution of hop lengths appears to be
@@
 
-  % BJC: Is it worth showing performance of both types of models? one mode versus two mode?
-  % Probably worth showing that 1 state fails
-  % BJC: also not sure if there is a better word than mode. I stayed away from 'state' since
-  % it's used heavily in the MSM section.
-  % BJC: I haven't created the 2 mode model yet, but that'll only take a few hours. I'll
-  % do that after I get BCC equilibrations running
   In general, we observe different dynamical behavior when solutes move inside the
   pore versus in the tail region.
-
   %MRS: could present the two models sequentiually.  Talk about one COULD have multiple modes, then in results present 1, then 2. 
-
   \begin{itemize}
@@
 
-  % BJC: can ignore this section for now. 
-  \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}  %BJC: potentially a separate paper
+  \subsection{Markov State Models}\label{method:MSMs}
 
-  Hidden Markov models (HMMs) are a useful and widely used technique
-  for modeling sequences of observations where the probability of the next observation
-  in a sequence depends only on a previous unobserved, or hidden, state.~\cite{beal_infinite_2002}
+  A Markov state model (MSM) decomposes a time series into a set of discrete states
+  with transitions between states defined by a transition probability matrix, T,
+  which describes the conditional probability of jumping to a specific 
+  state given the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
   \begin{itemize}
-    \item In the context of our simulations, the observations correspond to 
-    the center of mass coordinates of the solutes versus time, and the states
-    correspond to the dynamical behavior which give rise to those types
-    of observations.
-    \item Unfortunately, standard HMMs require the number of hidden states to be known
-    a priori.
-    \item One can partially overcome this by testing a range of numbers of 
-    hidden states and determining which is the best representation of their
-    data.
+% BJC1: moved following to intro
+%    \item In the context of molecular simulations, MSMs are frequently used
+%    to study systems with slow dynamics, such as protein folding.~\cite{snow_how_2005,chodera_automatic_2007}
+%    \item Researchers typically aim to come up with a low dimensional 
+%    representation of the system based on features which preserve the process
+%    kinetics. This facilitates the identification of discrete states from
+%    which T is generated.
+    \item Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011}
+    and pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable 
+    of featurization and dimensional reduction.
   \end{itemize}
 
-  The infinite-state HMM overcomes this drawback by placing a hierarchical
-  Dirichlet process (HDP) prior on the transition probabilities.
+  In this work, we define a total of 8 discrete states based on the 3 trapping
+  mechanisms observed in our previous work. 
   \begin{itemize}
-    \item Using some base probability distribution, H, a Dirichlet process 
-    (DP) generates distributions over a countably infinite number of 
-    probability measures:
-    \begin{equation}
-      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
-    \end{equation}
-    where the $\theta_k$ are values drawn from the base distribution and the
-    weights $\beta_k$ come from a stick-breaking process parameterized by the concentration 
-    parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). 
-    \item The concentration parameter expresses one's confidence in H relative to the posterior 
-    and is closely related to the number of data observations.
-    \item Each row, $G_j$, of the transition matrix is produced by drawing from a DP specified 
-    using the $\beta$ vector as a discrete base distribution and a separate concentration
-    parameter, $\alpha$.
-    \begin{equation}
-      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
-    \end{equation}
-    \item This hierarchical specification ensures that the transition probabilities in 
-    each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
-    \item Once the model has converged only a finite number of states will have significant
-    sampling.
+  	\item Therefore, there is no need to subject our trajectories to any reduction
+  	in dimensionality. 
+  	\item However, we will adopt the validation techniques used in the packages
+  	mentioned above.  
+  	%BJC: not sure the best way to lay these out
+  	\item The states we've chosen include all combinations of trapping mechanisms 
+  	in the pore and out of the pore:
+    \begin{table}[!htb]
+	  \centering
+	  \begin{tabular}{ll}
+	  \hline
+	  1. In tails                                  & 5. In pores                                  \\
+	  2. In tails and hydrogen bonding             & 6. In pores and hydrogen bonding             \\
+	  3. In tails and associated with sodium       & 7. In pores and associated with sodium       \\
+	  4. In tails, hydrogen bonding and associated & 8. In pores, hydrogen bonding and associated \\
+	  \hline
+	  \end{tabular}
+	  \caption{}\label{table:water_content}
+   \end{table}
+%  	\begin{enumerate}
+%  	  \item Trapped in tails
+%  	  \item Trapped in tails and hydrogen bonding
+%  	  \item Trapped in tails and associated with sodium
+%  	  \item Trapped in tails, hydrogen bonding and associated
+%  	  \item In pores
+%  	  \item In pores and hydrogen bonding
+%  	  \item In pores and associated with sodium
+%  	  \item In pores, hydrogen bonding and associated
+%  	\end{enumerate}
+  	\item These choices assume that there are no significant kinetic effects resulting
+  	from solute conformational changes or pore size fluctuations, an assumption 
+  	that may be relaxed in future work.
   \end{itemize}
 
-  \noindent We describe the dynamics of each state using a vector autoregressive (VAR) model. 
+  % BJC: does it make sense to use Dirichlet Process as a conjugate prior for
+  % getting error on transition matrix?
+  % BJC1: aha yes! \cite{bacallado_bayesian_2009}
+
+  \noindent We constructed a state transition probability matrix based on observed solute
+  trajectories.
   \begin{itemize}
-  	\item A VAR process is characterized by a vector of observations in a time series 
-  	that are dependent on $r$ previous values of the time series vector, weighted by a
-  	coefficient matrix $A_i$ in addition to a white noise term $\mathbf{e}_t$:
-  	\begin{equation}
-  	\mathbf{y}_t = \sum_{i=1}^r A_i\mathbf{y}_{t-i} + \mathbf{e}_t~~~~\mathbf{e}_t \sim N(0, \Sigma)
-  	\end{equation}
-  	\item We assumed multivariate Gaussian noise and limited our analysis to an 
-  	autoregressive order of $r=1$.
-  	\item We used a conjugate matrix-normal inverse-Wishart prior on parameters
-  	$A$ and $\Sigma$ in order to analytically draw from the posterior.
+    \item Using methods described in our previous work, we determined 	
+    which, if any, trapping mechanisms affected the solute at each time step, and
+    assigned the observation to a specific state according to the definitions 
+    above.~\cite{coscia_chemically_2019}
+    \item Based on the current and previous state observation, we incremented the
+    appropriate entry of an $n~\times~n$ count matrix by 1, where $n$ is the number of states.
+    \item For example, if we observed state 1 followed by a transition to state 3,
+    we increment the $(1, 3)$ entry of the count matrix by 1.
+    \item We generate the transition probability matrix from the count matrix by 
+    normalizing the entries in each row so that they summed to unity.
   \end{itemize}
 
-  Based on the VAR parameters and matrix of transition probabilities, we calculated
-  the most likely sequence of hidden states.
+  \noindent We recorded the $z$-direction displacement at each time step in order to construct
+  individual emission distributions for each state and transition between states.
   \begin{itemize}
-    \item We repeated this process iteratively until we reached convergence % BJC: need to define convergence criteria
-    \item Our python implementation of this process is heavily adapted from the MATLAB code
-    of Fox et al.~\cite{fox_sticky_2007} 
-    \item We refer the interested reader to much more extensive descriptions of 
-    this process and its implementation. 
-    ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
+    \item This is where we have modified the standard MSM framework.
+    \item While the dynamics of the states themselves are important, the 
+    majority of observations involve transitions between states, so properly modeling
+    the transition dynamics is even more important.
+    \item This results in 64 distinct emission distributions. Some are far more
+    populated than others. % BJC1: need to look into lumping transition emissions into one distribution
+    %\item The shape of the distributions are symmetric and heavy-tailed. 
   \end{itemize}
-  \break
+
+  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
+  \begin{itemize}
+    \item For independent and identically distributed (iid) random variables, the 
+    generalized central limit theorem guarantees convergence of the associated 
+    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
+    % BJC: ``For sums of independent, iid random variables with proper normalization to the
+%    sample size, the generalized central limit theorem guarantees the convergence of
+%    the associated PDF to a L\'evy stable PDF even though the variance of these random
+%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
+    \item The characteristic equation describing the Fourier transform of a L\'evy 
+    stable PDF is given below:
+    \begin{equation}
+    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
+    \end{equation}
+    \item Where $\omega$ is defined with something that is complicated to format and can be 
+    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
+    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
+    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
+    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
+    functions, is the Gaussian PDF ($\alpha$ = 2).
+    \item The more general family of L\'evy stable distributions allows
+    greater flexibility in defining the observed emission distribution PDFs.
+    \item In the case that the empirical emission distributions are iid, sequential draws
+    from a L\'evy stable PDF defines a L\'evy process. 
+    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
+    probability distributions if we instead consider the dynamics to be governed by a
+    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
+    \item OU processes contain temporal dependence but the marginal observation distributions
+    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
+    \item We will discuss the implications of each.  
+    % MRS: does the process described above include the motion within the state? That is something I feel that the
+    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
+    % BJC1: Right, I added a sentence to the paragraph before this one to make it clear that we
+    % are adding to the standard MSM.
+  \end{itemize}
+
+  % BJC: quote from anomalous diffusion book:
+  % "While the continuous time random walk model for Levy flights ... is a
+  % conventient description, in all other cases the fraction Fokker-Planck or,
+  % equivalently, the Langevin equation with white Levy stable noise are the 
+  % description of choice" -- pretty sure this is exactly what I'm suggesting above.
+
+  L\'evy stable distributions often have heavy tails and an undefined variance 
+  which can give rise to arbitrarily long particle displacements.
+  \begin{itemize}
+  	\item We do not observe hops longer than x nm in our simulations which 
+  	emphasizes that these distributions are only an approximation.
+    \item We avoid enormous and unrealistic hops problem by truncating the tails
+    of the distribution. %BJC: can add some citations about truncated Levy distributions which are used frequently in modeling
+    \item Since solutes in our system cannot hop further than the length of our 
+    simulation unit cell, we truncate the tails of the distribution at this
+    magnitude.
+    % BJC: Is this actually the right way to do this? I am looking at unwrapped coordinates,
+    % so theoretically a particle can move as far as it wants between frames.
+    % BJC: The cut-off choice is pretty important and has a significant effect on MSD. 
+    % For example, if I truncate at the unit cell length I reproducably get a final MSD of ~ 66 nm^2 (1000 ns stochastic simulation)
+    % If I truncate the tails at double the unit cell length, I get a final MSD of ~107 nm^2
+    % The uncertainty also increases (since variance diverges for these distributions)
+    % So maybe it makes the most sense to truncate based on largest observed hops.
+    % BJC1: Okay, plan is: longest observed hop when generating realizations to match MD MSDs
+    % BJC1: Use longest expected hop based on bulk diffusion for long timescale projections.
+  \end{itemize}
+
+  We simulated realizations of the stochastic process using the probability transition
+  matrix and emission distributions.
+  \begin{itemize}
+    \item For each trajectory simulated, we chose an initial state randomly from a 
+    uniform distribution. %BJC: could construct initial distribution but I'm not sure how reliable that is based on 24 solutes that are started in the pore center.
+    \item We randomly drew subsequent state transitions and corresponding emissions 
+    from the rows of the probability transition matrix and the appropriate emission
+    distribution respectively.
+  \end{itemize}
+
+  %BJC: need to add some validation of Markovian behavior and time step choice.
+
   \section{Results and Discussion}
@@
   %MRS: I'm not sure where the below is different from what was found in the previous study (i.e MSD's).
-  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
-  previous work.
+  % BJC1: move to supporting if included
+%  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
+%  previous work.
+%  \begin{itemize} 
+%    \item The extent to which each trapping mechanism influences each solute is
+%  	depicted graphically in Figure TBD.
+%    \item Same types of figures from transport paper:
+%    \item Fraction participating in hydrogen bonds, fraction associated, fraction
+%    in the tails.
+%    \item Lifetimes of hbonds and sodium associations?
+%  \end{itemize}
+
+  Methanol and acetic acid are not fully equilibrated, therefore we did not use them
+  to test our models.
+
+  \subsection{Subordinated Fractional Brownian Motion Modeling}\label{section:sFBM}
+
+  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
+  of $\sigma$, $\alpha$ and $H$ for each solute for the 1 and 2 mode models 
+  (see Table~\ref{table:sfbm_params}).
   \begin{itemize}
-    \item The extent to which each trapping mechanism influences each solute is
-  	depicted graphically in Figure TBD.
-    \item Same types of figures from transport paper:
-    \item Fraction participating in hydrogen bonds, fraction associated, fraction
-    in the tails.
-    \item Lifetimes of hbonds and sodium associations?
+    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
+    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values . 
+  	\item Higher values of $\sigma$ indicate larger average hop lengths.
+  	\item Higher values of $\alpha$ mean that there will be less sampling of 
+  	long dwell times.
+  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
+  	of anti-correlation.
+  	\item All of which contribute to an overall increase in the MSD.
   \end{itemize}
+
+  % BJC: this is a placeholder.
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{cccc}
+  \toprule
+  System & $\sigma$ ($nm$) & $\alpha$ & $H$ \\
+  \midrule
+  Methanol & 0.46 & 0.85 & 0.40 \\
+  Urea & 0.33 & 0.64 & 0.40 \\
+  Ethylene Glycol & 0.35 & 0.64 & 0.36 \\
+  Acetic Acid & 0.28 & 0.51 & 0.44 \\
+  \bottomrule
+  \end{tabular}
+  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
+  trajectories and then computed the average ensemble-averaged MSD of 10000 
+  simulated trajectories.}\label{table:sfbm_params}
+  \end{table}
+
+  \noindent We compared the MSD of simulated sFBM trajectories to MD simulated
+  MSDs.
+  \begin{itemize}
+	\item We simulated 10000 sFBM trajectories of the same length as our MD
+	simulations, as described in Section~\ref{method:model_sFBM} of the Methods.
+	\item The final MSDs of the sFBM trajectories are compared to those 
+	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
+	\item We would like to emphasize that we rely on the MD MSD values in order to
+	define trends in the total MSD, while the sFBM trajectories and parameter 
+	values allow us to speculate as to the reasons for the observed trends. 
+	\item There is a non-negligible amount of error in the calculation of 
+	each parameter which prevents us from reliably portraying our sFBM MSDs as
+	reduced	uncertainty MD MSDs.
+	% BJC: I think it's more the power law tails that increases uncertainty.
+  \end{itemize}
+
+  % BJC1: yea we'll see
+  The two-mode sFBM model does a better job than the one-mode model at 
+  reproducing the MD MSD trends. 
+  \begin{itemize}
+    \item One-mode model generally undershoots MSDs.
+  \end{itemize}
+
+  %BJC: reduce this figure to solutes studied and put 3 bars for each solute: MD MSD, one-mode sfbm MSD, two-mode sfbm MSD
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{all_emsds.pdf}
+  \caption{}\label{fig:all_msds}
+  \end{figure}
 
@@
     series describing each state.
-    \item Therefore we did not do this and attempted to fit a different model. 
+    % \item Therefore we did not do this and attempted to fit a different model. 
     %BJC: we could add some artificial correlation to prove the anti-correlation hypothesis
   \end{itemize}
-
-  \subsection{Subordinated Fractional Brownian Motion Modeling}\label{section:sFBM}
-
-  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
-  of $\sigma$, $\alpha$ and $H$ for each solute for the 1 and 2 mode model 
-  (see Table~\ref{table:sfbm_params}).
-  \begin{itemize}
-    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
-    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values . 
-  	\item Higher values of $\sigma$ indicate larger average hop lengths.
-  	\item Higher values of $\alpha$ mean that there will be less sampling of 
-  	long dwell times.
-  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
-  	of anti-correlation.
-  	\item All of which contribute to an overall increase in the MSD.
-  \end{itemize}
-
-  % BJC: worth including single parameter model (i.e. no radial dependence) to 
-  % show its shortcomings? Or send to supporting information
-  % BJC: obviously still needs 2 mode data
-  % BJC: this is 1 microsecond data
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{cccc}
-  \toprule
-  System & $\sigma$ ($nm$) & $\alpha$ & $H$ \\
-  \midrule
-  Methanol & 0.46 & 0.85 & 0.40 \\
-  Urea & 0.33 & 0.64 & 0.40 \\
-  Ethylene Glycol & 0.35 & 0.64 & 0.36 \\
-  Acetic Acid & 0.28 & 0.51 & 0.44 \\
-  \bottomrule
-  \end{tabular}
-  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
-  trajectories and then computed the average ensemble-averaged MSD of 10000 
-  simulated trajectories.}\label{table:sfbm_params}
-  \end{table}
-
-  \noindent We compared the MSD of simulated sFBM trajectories to MD simulated
-  MSDs.
-  \begin{itemize}
-	\item We simulated 10000 sFBM trajectories of the same length as our MD
-	simulations, as described in Section~\ref{method:model_sFBM} of the Methods.
-	\item The final MSDs of the sFBM trajectories are compared to those 
-	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
-	\item We would like to emphasize that we rely on the MD MSD values in order to
-	define trends in the total MSD, while the sFBM trajectories and parameter 
-	values allow us to speculate as to the reasons for the observed trends. 
-	\item There is a non-negligible amount of error in the calculation of 
-	each parameter which prevents us from reliably portraying our sFBM MSDs as
-	reduced	uncertainty MD MSDs.
-	% BJC: I think it's more the power law tails that increases uncertainty.
-  \end{itemize}
-
-  The two-mode sFBM model does a better job than the one-mode model at 
-  reproducing the MD MSD trends. 
-  \begin{itemize}
-    \item One-mode model generally undershoots MSDs.
-  \end{itemize}
-
-  %BJC: reduce this figure to solutes studied and put 3 bars for each solute: MD MSD, one-mode sfbm MSD, two-mode sfbm MSD
-  \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{all_emsds.pdf}
-  \caption{}\label{fig:all_msds}
-  \end{figure}
 

### 2019-09-04 Ben_Manuscripts/stochastic_transport/Outline.tex
updated outline.
Nailing down transport models + documenting them

@@
 
-%MRS: better to have the first outline shorter to iterate more quickly!
-%BJC1: right, this one has been in the works for a while now. Wrote the anomalous diffusion methods a long time ago
-
 %MRS: better to have a title that described a finding, rather than the
@@
 %MRS: also 'stochastic modeling' is pretty vague.  should be more precise. 
-\title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 %MRS: we should discuss whether Chris Calderon would be on this one.  I would guess no, but I don't know for sure. 
@@
 %me towards Greg Morrin who pointed me towards useful anomalous diffusion literature.
+%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   \section{Introduction}
-  %BJC: obviously this section will get beefed up
+
+  % MRS1: I would start with something more central to the content of the paper - how do solutes move in complex separations membranes?
+Let people know right from the start what the paper is about.
+This paragraph should still be in the intro, but start with something that captures the main question of the paper.
+  % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
+  Mathematical descriptions of transport in complex separations membranes are a powerful 
+  way to understand mechanisms and formulate membrane design principles.
+  \begin{itemize}
+    \item The complexity of a model generally parallels the complexity of the 
+    transport mechanism at hand, as well as the desired outputs.
+    \item In dense homogeneous membranes, the solution-diffusion model can extract
+    diffusion and partition coefficients and has successfully predicted solute transport
+    rates.
+    \item Analogously, pore-flow models yield predictions of diffusion coefficients
+    and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
+    \item Single particle tracking allows us to further characterize more complex
+    diffusive behavior.
+    \item Finally, Molecular simulation provides a framework for studying both single
+    particle dynamics and bulk transport properties with atomic resolution.
+    \item All of these approaches facilitate speculation on the molecular origins of
+    separations and suggest experiments that should be run by attempting to give a more
+    intuitive understanding of how solutes move as a function of their environment.
+%    \item The hydrodynamic Ferry model is the simplest pore-flow model, with extensions such
+%    as the Donnan-Steric Pore Model which includes extra terms for the pressure gradient
+%    across the membrane and membrane charge.
+%    \item Dischinger et al. created an empirical correlation to determine the
+%    effect of solute physicochemical properties on solute rejection.
+  \end{itemize}
+
+%  \begin{itemize}
+%    \item More recently, rapid advancements in computational power have made it feasible
+%    to observe transport in simulated systems with atomic resolution. This allows us to
+%    shift towards analysis of the motion of individual particles and gives an even more 
+%    fundamental understanding of observed bulk properties.
+%  \end{itemize}
+
+  % BJC1: tie this paragraph into above by commenting that highly selective membranes
+  % often have complex mechanistic reasons that aren't explained by simpler models
   We need highly selective membranes in order to perform efficient separations. \\
@@
   Lyotropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
-  into mechanically strong membranes.
+  into mechanically strong and highly selective membranes.
   \begin{itemize}
@@
 
+  % BJC2: moved this from below
+  Our first modeling approach is based on the anomalous diffusion literature, applying the 
+  mathematical formalism describing subdiffusive transport to observed solute 
+  trajectories.
+  \begin{itemize}
+    \item We determine the most likely subdiffusive mechanisms at play using the 
+    flow chart in figure X. 
+    \item We then fit anomalous diffusion models in two ways: First, based on a
+    single set of parameters. Second, we use a two-state approach incorporating
+    two sets of parameters based on a solute's radial distance from the pore center. 
+  \end{itemize}
+
   While elegant, pure anomalous diffusion theory may in some cases give only a qualitative
@@
   	in the tails.
-  	\item We can use the anomalous diffusion approach to model to our data as a 
+  	\item We can use the anomalous diffusion approach to model our data as a 
   	function of radial distance from the closest pore center.
@@
 
+  %MRS1: probably want to make clear that you really are doing some
+  %substantially different things in in MSM modeling than most people
+  %do, by adding on modeling the z-diffusion as an auxiliary variable
+  %of the state.  I think that's actually kind of innovative.
+
+  %BJC2: moved this paragraph up from below to clarify novelty of this approach
+  Our second modeling approach adapts the MSM framework to a relatively small set
+  of known states based on the three observed solute trapping mechanisms.
+  \begin{itemize}
+    \item Standard MSMs assume first order kinetics and are typically applied 
+    towards determining equilibrium populations of various state configurations.
+    \item We extend the framework to include dynamics within states and
+    between jumps. 
+    \item That is we incorporate the magnitude and temporal dependence of the 
+    time series fluctuations between each transition to a different state. 
+    \item Temporal dependence has a significant influence on mean squared displacement.
+  \end{itemize}
+
   In this work we attempt to model the long timescale behavior of the four 
@@
   	% require anything different in systems with more complex geometries (i.e. QI)
-  \end{itemize}
-
-  Our first approach is based on the anomalous diffusion literature, applying the 
-  mathematical formalism describing subdiffusive transport to observed solute 
-  trajectories.
-  \begin{itemize}
-    \item We determine the most likely subdiffusive mechanisms at play using the 
-    flow chart in figure X. 
-    \item We then fit anomalous diffusion models in two ways: First, based on a
-    single set of parameters. Second, we use a two-state approach incorporating
-    two sets of parameters based on a solute's radial distance from the pore center. 
-  \end{itemize}
-
-  The second approach adapts the MSM framework to a relatively small set of known 
-  states based on the three observed solute trapping mechanisms.
-  \begin{itemize}
-    \item We extend the framework to include dynamics between jumps. 
-    \item That is we incorporate the magnitude and temporal dependence of the 
-    time series fluctuations between each transition to a different state. 
-    \item Temporal dependence has a significant influence on mean squared displacement.
   \end{itemize}
@@
 
-  % MRS: you intend this to be a separate model than the above?  If so, make clearer.
-  % BJC1: renamed, is that what you meant?
   \subsection{The Anomalous Diffusion Model}\label{method:model_sFBM}
@@
   % interest of simplicity, maybe leave it at Gaussian.
+  % BJC2: This will change to Levy. 
   For solutes in our system, the distribution of hop lengths appears to be
@@
 	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
+        %MRS1: can just say bootstrapping.
   \end{itemize}
@@
   \subsection{Markov State Models}\label{method:MSMs}  
+  % BJC2: still need a better name
+  % name candidates - correlated MSMs, Dynamical mode switching
 
@@
   	in the pore and out of the pore:
+        %MRS: ``1. in tails and 5. in pores seem to encompass the things below them. Maybe us ``in tails, not trapped,'' etc. as the last entry in each column.'' 
+        %BJC2: good point
     \begin{table}[!htb]
@@
 	  \hline
-	  1. In tails                                  & 5. In pores                                  \\
+	  1. In tails, not trapped                     & 5. In pores, not trapped                     \\
 	  2. In tails and hydrogen bonding             & 6. In pores and hydrogen bonding             \\
@@
 
+  % BJC2: An abbreviated from of this paragraph probably belongs in previous section
+  % since I'll be using subordinated levy motion.
   \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
@@
     non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
+    %MRS1: you many consider putting some of the long explanations in supporrting. 
     \item OU processes contain temporal dependence but the marginal observation distributions
@@
 
-  %BJC: need to add some validation of Markovian behavior and time step choice.
+  % BJC: need to add some validation of Markovian behavior and time step choice.
 
@@
   Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
-  of $\sigma$, $\alpha$ and $H$ for each solute for the 1 and 2 mode models 
+  of $\sigma$, $\alpha$, $H$ and $\lambda$ for each solute for the 1 and 2 mode models 
   (see Table~\ref{table:sfbm_params}).
@@
     \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
-    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values . 
+    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values. 
   	\item Higher values of $\sigma$ indicate larger average hop lengths.
@@
   	long dwell times.
+  	\item Higher values of $\lambda$ truncates the power law distribution earlier
+  	preventing extremely long dwell times.
   	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
@@
 
-  \noindent We compared the MSD of simulated sFBM trajectories to MD simulated
+  % BJC2: Adding all combinations of distributions.
+  % Power law + Gaussian, Power law + Levy, Power law w/cutoff + Gaussian, Power Law w/cutoff + Levy
+  % BJC2: Probably a good idea to at least mention results when no anitcorrelation is included
+  \noindent We compared the MSD of simulated sFBM and sFLM trajectories to MD simulated
   MSDs.
@@
 	values allow us to speculate as to the reasons for the observed trends. 
-	\item There is a non-negligible amount of error in the calculation of 
-	each parameter which prevents us from reliably portraying our sFBM MSDs as
-	reduced	uncertainty MD MSDs.
+%	\item There is a non-negligible amount of error in the calculation of 
+%	each parameter which prevents us from reliably portraying our sFBM MSDs as
+%	reduced	uncertainty MD MSDs.
 	% BJC: I think it's more the power law tails that increases uncertainty.
+	% BJC2: Error looks relatively small now.
   \end{itemize}
 
-  % BJC1: yea we'll see
-  The two-mode sFBM model does a better job than the one-mode model at 
-  reproducing the MD MSD trends. 
+  % BJC2: A qualitative comparison of sFLM trajectories to MD trajectories might be nice.
+
+  \noindent The power law with exponential cut-off has the largest effect on the on 
+  the match between MD MSD and sFLM trajectories.
   \begin{itemize}
-    \item One-mode model generally undershoots MSDs.
+    \item Using the power law with cutoff produces predictions in relatively good agreement
+    with MD.
   \end{itemize}
 
-  %BJC: reduce this figure to solutes studied and put 3 bars for each solute: MD MSD, one-mode sfbm MSD, two-mode sfbm MSD
+  \noindent The choice between Levy and Gaussian distributions has only a small effect, 
+  but the Levy appears to fit emission distributions better.
+
+  % BJC: reduce this figure to solutes studied and put 3 bars for each solute: MD MSD, 
+  % one-mode sfbm MSD, two-mode sfbm MSD.
+  % BJC2: Actually I think I prefer showing the MSD curves on one plot, like in my research journal. Since it shows shape.
   \begin{figure}
@@
 
+  \noindent We can use the model to project our simulations out to very long timescales.
+  \begin{itemize}
+    \item We can not definitively say which combination of distributions are best to use.
+    \item Although the longest observed dwell times and hop lengths are less than
+    the length of the simulated trajectories and box lengths respectively, it is still possible
+    that that extremely long dwell times and hops are observed experimentally in rare but
+    significant cases.
+    \item We present long timescale projections using combinations of each distribution in the
+    table below
+  \end{itemize}
+
+  % BJC2: table of long timescale projections using combinations of dwell and hop distributions. 
+  %% TABLE %%
+
   \subsection{Markov State Model Fits}\label{section:msm_results}
+  % BJC2: This section should parallel the previous section in terms of presentation of results.
+
+  We constructed emission distributions which correspond to each entry in the transition
+  matrix.
+  \begin{itemize}
+    \item Some states are sampled far more frequently than other leading to better converged
+    distributions.
+  \end{itemize}
 
@@
   \begin{itemize}
-    \item The heavy tails of the distribution are a consequence of hopping.
+    %\item The heavy tails of the distribution are a consequence of hopping.
     \item Heavily sampled states fit well to L\'evy stable distributions.
@@
 
-  % BJC: need better or more descriptive way of describing stochastic simulations
-  % BJC: or could say that whenever we say simulations, we mean stochastic simulations unless it is specified as a molecular dynamics simulation.
-  % MRS: could say timeseries simulation?  MD is stochastic as well.
-  Simulating solute trajectories (see Section~\ref{method:MSMs}) by drawing independent  
-  observations from the emission distributions yields near linear MSD curves
-  with final values that are far higher than those observed in our molecular simulations.
+  % BJC2: I need to look into the motion when a solute is trapped. It should have a very low H.
+  \noindent Motion within states is anticorrelated. 
   \begin{itemize}
-	% BJC: right number of solute trajectories to simulate for comparison? More tightens the error bars
-    \item In the case of methanol, the final MSD value is about 25x higher than that observed in our
-    previous transport study (see Figure~\ref{fig:msd_MET}).
-    \item The linear behavior of the MSD curve is not consistent with subdiffusion.
+    \item We calculated the self-similarity parameter for motion within each state.
   \end{itemize}
-  %MRS: so, is there a way we should have been able to tell beforrehand that this approach didn't work that we an explain?
-  %or can we show we needed to do this to get the results?
-  %BJC1: could just show autocorrelation function of all increments, which has negative dip at k=1 
+
+  \noindent The emissions resulting from transitions between states are anticorrelated.
+  \begin{itemize}
+    \item We simulated these emissions by combining all transition emissions into a single
+    distribution with a single self-similarity parameter.
+    \item We are unaware of techniques for simulating correlated draws from L\'evy distributions
+    with varying shapes.
+  \end{itemize}
+
+  % BJC2: Could explore a second model with an emission distribution for transitions in tails versus pores.
+
+  % BJC2: FIGURE: autocorrelation of motion while trapped in a state and autocorrelation of emissions.
+
+  % BJC2: This figure will show predicted MSDs versus MD MSDs
   \begin{figure}[!h]
@@
 
-  \noindent Anti-correlation between hops may be responsible for subdiffusive behavior.
-  \begin{itemize}
-    \item In general, we observe negative correlation between hops.
-    \item A L\'evy driven OU process may be a more appropriate way to model
-    the stochastic dynamics of this system since you can incorporate autocorrelation.
-    \item Extracting reliable correlation functions is difficult with our data
-    due to relatively frequent switching resulting in sets of short disjoint time 
-    series describing each state.
-    % \item Therefore we did not do this and attempted to fit a different model. 
-    %BJC: we could add some artificial correlation to prove the anti-correlation hypothesis
-  \end{itemize}
+%  \noindent Anti-correlation between hops may be responsible for subdiffusive behavior.
+%  \begin{itemize}
+%    \item In general, we observe negative correlation between hops.
+%    \item A L\'evy driven OU process may be a more appropriate way to model
+%    the stochastic dynamics of this system since you can incorporate autocorrelation.
+%    \item Extracting reliable correlation functions is difficult with our data
+%    due to relatively frequent switching resulting in sets of short disjoint time 
+%    series describing each state.
+%    % \item Therefore we did not do this and attempted to fit a different model. 
+%    %BJC: we could add some artificial correlation to prove the anti-correlation hypothesis
+%  \end{itemize}
+
+  We projected the long timescale behavior using this model. 
+  %BJC2: TABLE. 
+  %BJC2: Would probably be best to combine this with table from anomalous diffusion.
 
   \section{Conclusion}
+
+  % MRS1: will want to make a stateemnt about whether these approaches
+  % are together good enough for predictive purposes, and if not,
+  % explore what else should be done in the future.
+  % BJC2: It seems like it would be hard to make say these can be used
+  % for prediction without experimental confirmation of the trends that we observe.
 
@@
   \begin{itemize}
+    \item Subordinated fractional Brownian motion has a nice theoretical foundation
+    in the anomalous diffusion literature. A two mode model that describes dynamics
+    based on whether a solute is in or out of the pore region leads to MSDs fairly
+    consistent with MD simulated trajectories.
     \item Markov state modeling with predefined states gives a nice description
@@
     time series behavior leading to overpredicted MSDs.
-    \item Subordinated fractional Brownian motion has a nice theoretical foundation
-    in the anomalous diffusion literature. A two mode model that describes dynamics
-    based on whether a solute is in or out of the pore region leads to MSDs fairly
-    consistent with MD simulated trajectories.
   \end{itemize}

### 2019-09-04 LLC_Membranes/timeseries/ctrwsim.py

@@ -4,12 +4,13 @@ import argparse
 import numpy as np
 import tqdm
 import sys
-from LLC_Membranes.llclib import timeseries, fitting_functions, stats, sampling
+from LLC_Membranes.llclib import timeseries, fitting_functions, stats, rand
 from LLC_Membranes.analysis import Poly_fit
 import matplotlib.pyplot as plt
 from multiprocessing import Pool
 import time as timer
 import fbm
+from LLC_Membranes.timeseries.fractional_levy_motion import FLM
 
 
 def initialize():
@@ -55,11 +56,11 @@ class CTRW(object):
                  lamb=0.5, padding=10, dt=1, nt=1, H=0.5, transition_matrix=None):
         """ Initialize simulation of a continuous time random walk
 
-        :param length: length of each simulated trajectory. If you fix the number of steps, this equals the number of
+        :param length: length of each simulated trajectory. If you fix the number of steps, this equals the number of \
         steps. If you fix the time, the total length of the simulation is length * dt
         :param ntraj: number of independent trajectories to generate
         :param nmodes: number of modes. There should be sigma, alpha and H parameters for each mode
-        :param hop_dist: Method used to generate random hop lengths. "gaussian" draws randomly from a gaussian
+        :param hop_dist: Method used to generate random hop lengths. "gaussian" draws randomly from a gaussian \
         distribution, while "fbm" generates correlated hops as in fractional brownian motion.
         :param dwell_dist: Name of probability distribution function used to generate random dwell times
         :param hop_sigma: Sigma for Gaussian hop_dist random draws
@@ -68,9 +69,9 @@ class CTRW(object):
         :param padding: multiplies number of discrete time points used to interpolate trajectories
         :param dt: time step for fixed time simulations
         :param nt: number of threads to use where parallelized
-        :param H: Hurst parameter for fractional brownian motion. Equals 2*alpha for pure FBM. For H < 0.5, trajectories
-        are subdiffusive, when H = 0.5, brownian motion is recovered.
-        :param transition_matrix: nmode x nmode matrix of transition probabilties between states. Only needed if
+        :param H: Hurst parameter for fractional brownian motion. Equals 2*alpha for pure FBM. For H < 0.5, \
+        trajectories are subdiffusive, when H = 0.5, brownian motion is recovered.
+        :param transition_matrix: nmode x nmode matrix of transition probabilties between states. Only needed if \
         nmodes > 1.
 
         :type length: int
@@ -93,9 +94,9 @@ class CTRW(object):
[…]

### 2019-09-04 docs/conf.py

@@ -26,6 +26,7 @@ sys.path.insert(0, os.path.abspath('../LLC_Membranes'))
 sys.path.insert(0, os.path.abspath('../LLC_Membranes/setup'))
 sys.path.insert(0, os.path.abspath('../LLC_Membranes/analysis'))
 sys.path.insert(0, os.path.abspath('../LLC_Membranes/llclib'))
+sys.path.insert(0, os.path.abspath('../LLC_Membranes/timeseries'))
 
 # -- General configuration ------------------------------------------------
 

### 2019-09-05 Ben_Manuscripts/stochastic_transport/Outline.tex
Some reorganization and more methods

@@
   % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
+  % BJC2: I'm not sure if this is exactly what you meant though
+%  Making sense of solute motion in complex separations membranes is central to 
+%  understanding transport mechanisms and formulating membrane design principles.
   Mathematical descriptions of transport in complex separations membranes are a powerful 
@@
   % often have complex mechanistic reasons that aren't explained by simpler models
-  We need highly selective membranes in order to perform efficient separations. \\
+  These approaches can be especially useful for designing highly selective membranes. \\
+  %BJC2: this paragraph will contain examples of highly selective separations
 
@@
   solute-specific separations.\\
+  %BJC2: simple models from first paragraph fail to adequately describe transport.
 
@@
   able to make well-converged predictions of macroscopic transport properties 
-  traditionally used to characterize membranes in the lab. \\
+  traditionally used to characterize membranes in the lab.
   \begin{itemize}
@@
 
-  \noindent We can use the observations of transport from our previous work in order to create 
-  state-based models.
-  \begin{itemize}
-  	\item We know that dynamics differ between solutes moving inside the pores and 
-  	in the tails.
-  	\item We can use the anomalous diffusion approach to model our data as a 
-  	function of radial distance from the closest pore center.
-  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
-  	methods of Markov state modeling.
-  \end{itemize}
+%  \noindent We can use the observations of transport from our previous work in order to create 
+%  state-based models.
+%  \begin{itemize}
+%  	\item We know that dynamics differ between solutes moving inside the pores and 
+%  	in the tails.
+%  	\item We can use the anomalous diffusion approach to model our data as a 
+%  	function of radial distance from the closest pore center.
+%  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
+%  	methods of Markov state modeling.
+%  \end{itemize}
 
@@
 
-  In this work we attempt to model the long timescale behavior of the four 
-  fastest moving solutes studied in our previous work.
+  In this work we apply the two modeling approaches in order to predict the long
+  timescale behavior of the four fastest moving solutes studied in our previous work.
   \begin{itemize}
@@
     and then to project the long-term dynamics of each solute. 
-    \item We explore two modeling approaches
 %  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
@@
   We ran all MD simulations and energy minimizations using GROMACS 2018. We  % needs gromacs citations
-  performed all post-simulation trajectory using python scripts which are available
+  performed all post-simulation trajectory analysis using python scripts which are available
   %MRS: eventually want to say what scripts were used to do what, but that is not at the outline stage!
@@
   \end{itemize}
+
+  We determined equilibration based on the solute partition between the pore and tail
+  region.
 
@@
   % justify the choice in model so I can write the methods about the chosen models
+  % BJC2: Perhaps just say that we think it's sFBM and move the proof to discussion.
   \noindent We believe that solutes in the system studied here exhibit subordinated 
@@
 	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
-	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
-        %MRS1: can just say bootstrapping.
+	$\alpha$ using bootstrapping.\cite{efron_introduction_1994} 
   \end{itemize}
 
-  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
-  $H = \beta/2$.
+  In practical applications, the heavy tail of power law distributions can result in 
+  arbitrarily long dwell times that are never observed in MD simulations. 
+  \begin{itemize}
+    \item We can not observe dwell times longer than the length of a single trajectory.
+    \item In fact the longest dwell time observed by solutes in this study is X.
+    \item In order to compare our anomalous diffusion model to MD results we need to 
+    bound the dwell time distribution.
+    \item We do this by adding an exponential cut-off to the power law so the dwell 
+    time distribution is of the form:
+    \begin{equation}
+    t^{-1 - \alpha}e^{-\lambda t}
+    \end{equation}
+    \item We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
+    \begin{equation}
+    \mathcal{L}(\alpha, \lambda) = n*(1 - \alpha)ln\lambda - n*ln\Gamma(1 - \alpha, x_{min}\lambda) - \alpha\sum_{i=1}^{n}ln x_i - \lambda\sum_{i=1}^n x_i
+    \end{equation}
+  \end{itemize}
+
+  \noindent FBM processes can be described using the Hurst parameter, $H$.
   \begin{itemize}
@@
 	values. %BJC: can provide more detail in supporting or just reference python script
+	\item There are more complicated ways to calculate H but well-converged estimates 
+	require far more data than we have access to.
   \end{itemize}
 
-  In general, we observe different dynamical behavior when solutes move inside the
-  pore versus in the tail region.
+  \noindent If the distribution of hops is not Gaussian, we can model them with the
+  more general class of L\'evy stable distributions.
+  \begin{itemize}
+    \item For independent and identically distributed (iid) random variables, the 
+    generalized central limit theorem guarantees convergence of the associated 
+    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
+    % BJC: ``For sums of independent, iid random variables with proper normalization to the
+%    sample size, the generalized central limit theorem guarantees the convergence of
+%    the associated PDF to a L\'evy stable PDF even though the variance of these random
+%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
+    \item The characteristic equation describing the Fourier transform of a L\'evy 
+    stable PDF is given below:
+    \begin{equation}
+    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
+    \end{equation}
+    \item Where $\omega$ is defined with something that is complicated to format and can be 
+    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
+    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
+    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
+    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
+    functions, is the Gaussian PDF ($\alpha$ = 2).
+    \item We assume symmetric distributions centered about 0 implying that $\beta$ and $\mu$ are both 0.
+  \end{itemize}
+
+  \noindent If the hops are correlated, we can describe their motion as subordinated 
+  fractional L\'evy motion.
+  \begin{itemize}
+    \item The hurst parameter can again be used to describe the degree of anitcorrelation.
+    \item It has the form: %BJC2: need to see if there is an analytical form for H
+    %BJC2: might need to use a different way to estimate H (which is more standard): https://pypi.org/project/hurst/
+  \end{itemize}
+
+  In general, we observe different dynamical behavior when solutes move while inside 
+  the pore versus while in the tail region.
   %MRS: could present the two models sequentiually.  Talk about one COULD have multiple modes, then in results present 1, then 2. 
@@
   For the two mode model, we needed to define a probability transition matrix 
-  describing transitions between the tail and pore region.
+  describing transitions between the tail and pore region. \\
 
@@
 	distributions.
+	\item We use the python package \texttt{fbm} to simulate fractional Brownian motion and 
+	our own implementation of the algorithm by Stoev and Taqqu to simulation fraction L\'evy motion.~\cite{stoev_simulation_2004}
 	\item We propagated each trajectory until the total time equaled or exceeded 5 $\mu$s, 
@@
     a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
-    \item We reported the MSD after 5 $\mu$s with corresponding 95 \% intervals
+    \item We reported the time-averaged MSD after 2 $\mu$s time lags with corresponding 
+    95 \% intervals
 % Following probably better suited for supporting information, if included at all
@@
     populated than others. % BJC1: need to look into lumping transition emissions into one distribution
+    \item We modeled the emission distributions as L\'evy stable distributions. 
     %\item The shape of the distributions are symmetric and heavy-tailed. 
@@
 
-  % BJC2: An abbreviated from of this paragraph probably belongs in previous section
+  % BJC2: Moved the meat of this paragraph to previous section
   % since I'll be using subordinated levy motion.
-  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
-  \begin{itemize}
-    \item For independent and identically distributed (iid) random variables, the 
-    generalized central limit theorem guarantees convergence of the associated 
-    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
-    % BJC: ``For sums of independent, iid random variables with proper normalization to the
-%    sample size, the generalized central limit theorem guarantees the convergence of
-%    the associated PDF to a L\'evy stable PDF even though the variance of these random
-%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
-    \item The characteristic equation describing the Fourier transform of a L\'evy 
-    stable PDF is given below:
-    \begin{equation}
-    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
-    \end{equation}
-    \item Where $\omega$ is defined with something that is complicated to format and can be 
-    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
-    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
-    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
-    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
-    functions, is the Gaussian PDF ($\alpha$ = 2).
-    \item The more general family of L\'evy stable distributions allows
-    greater flexibility in defining the observed emission distribution PDFs.
-    \item In the case that the empirical emission distributions are iid, sequential draws
-    from a L\'evy stable PDF defines a L\'evy process. 
-    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
-    probability distributions if we instead consider the dynamics to be governed by a
-    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
-    %MRS1: you many consider putting some of the long explanations in supporrting. 
-    \item OU processes contain temporal dependence but the marginal observation distributions
-    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
-    \item We will discuss the implications of each.  
-    % MRS: does the process described above include the motion within the state? That is something I feel that the
-    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
-    % BJC1: Right, I added a sentence to the paragraph before this one to make it clear that we
-    % are adding to the standard MSM.
-  \end{itemize}
+  \noindent  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
+%  \begin{itemize}
+%    \item For independent and identically distributed (iid) random variables, the 
+%    generalized central limit theorem guarantees convergence of the associated 
+%    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
+%    % BJC: ``For sums of independent, iid random variables with proper normalization to the
+%%    sample size, the generalized central limit theorem guarantees the convergence of
+%%    the associated PDF to a L\'evy stable PDF even though the variance of these random
+%%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
+%    \item The characteristic equation describing the Fourier transform of a L\'evy 
+%    stable PDF is given below:
+%    \begin{equation}
+%    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
+%    \end{equation}
+%    \item Where $\omega$ is defined with something that is complicated to format and can be 
+%    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
+%    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
+%    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
+%    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
+%    functions, is the Gaussian PDF ($\alpha$ = 2).
+%    \item The more general family of L\'evy stable distributions allows
+%    greater flexibility in defining the observed emission distribution PDFs.
+%    \item In the case that the empirical emission distributions are iid, sequential draws
+%    from a L\'evy stable PDF defines a L\'evy process. 
+%    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
+%    probability distributions if we instead consider the dynamics to be governed by a
+%    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
+%    %MRS1: you many consider putting some of the long explanations in supporrting. 
+%    \item OU processes contain temporal dependence but the marginal observation distributions
+%    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
+%    \item We will discuss the implications of each.  
+%    % MRS: does the process described above include the motion within the state? That is something I feel that the
+%    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
+%    % BJC1: Right, I added a sentence to the paragraph before this one to make it clear that we
+%    % are adding to the standard MSM.
+%  \end{itemize}
 
@@
     distribution respectively.
+    \item We added correlation between transitions as well as correlation to sequences
+    of emissions while dwelling in specific states.
   \end{itemize}
@@
 
-  \subsection{Subordinated Fractional Brownian Motion Modeling}\label{section:sFBM}
+  \subsection{Anomlaous Diffusion Modeling}\label{section:sFBM}
+
+  %BJC2: I think it makes sense to show the data supporting that this is likely
+  % sFBM here in the discussion. The methods would just point here.
+  We determined that transport is likely governed by sFBM using the flow chart in
+  Figure X.
+  \begin{itemize}
+    \item Show weak ergodicity breaking, non-stationarity and correlation between hops
+    \item Geometric argument against random walk on fractal?
+  \end{itemize}
 
@@
   \begin{itemize}
-    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
-    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values. 
+    \item In most cases, it is easy to relate the parameter values 
+    Table~\ref{table:sfbm_params} to the simulated MSD values. 
   	\item Higher values of $\sigma$ indicate larger average hop lengths.
@@
   	long dwell times.
-  	\item Higher values of $\lambda$ truncates the power law distribution earlier
+  	\item Higher values of $\lambda$ truncate the power law distribution earlier
   	preventing extremely long dwell times.
@@
   \noindent The choice between Levy and Gaussian distributions has only a small effect, 
-  but the Levy appears to fit emission distributions better.
+  but the Levy appears to fit emission distributions better. \\
 
@@
 
-  \subsection{Markov State Model Fits}\label{section:msm_results}
+  \subsection{Markov State Modeling}\label{section:msm_results}
   % BJC2: This section should parallel the previous section in terms of presentation of results.
@@
   % parameters with the plots, as it's hard to tell how different they may or may not be.
+  % BJC2: This figure is just 1 microsecond of data
   \begin{figure}[!h]

### 2019-09-07 Ben_Manuscripts/stochastic_transport/Outline.tex
MRS3 comments.

@@
   way to understand mechanisms and formulate membrane design principles.
+  % MRS3: seems pretty good.
+We can tweak later when turning into text; I don't think that it will really affect the logic of the paper.
+The introduction will be important here to set the stage, but probably more of that will be in the next paragraph.
   \begin{itemize}
@@
     diffusive behavior.
-    \item Finally, Molecular simulation provides a framework for studying both single
+    \item Finally, molecular simulation provides a framework for studying both single
     particle dynamics and bulk transport properties with atomic resolution.
@@
 
-  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.\\
+  %MRS3: I'd omit next line (That I commented out); you talk about membranes above, so better to start the next paragraph talking about membranes.
+  %\noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.\\
 
@@
 	pores. They are easier to make.
-  \end{itemize}
-
-  We can only learn so much from experiment. MD can give us mechanistic insights with
+        %MRS3: probably want to put a more here about why we are studing these membranes, and what advantages they might have, and why transport in them is complicated.  
+  \end{itemize}
+
+  %MRS3: One missing connection between the above information and what is in the paper would be making the connection between MD simulations
+  %and mathematical modeling, using MD to provide/justify the fuctional form and/or some of the parameters for the model, 
+  %rather than just experiment.
+
+  %MRS3: a suggested tweak in language
+  %We can only learn so much from experiment. 
+  There are limitations to what we can learn from experiment about the atomistic details of transport.
+  MD can give us mechanistic insights with
   atomistic resolution so that we can intelligently design new membranes for 
@@
     association with sodium counter ions.
+    %MRS3: point out that they were all subdiffusive (unlike water)
   \end{itemize}
@@
     \begin{equation}
-	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
-	\beta\sum_{i=1}^{n} \text{ln}~x_i 
+      %MRS: use \ln instead of ln or \text{ln} 
+	\mathcal{L}(\beta) = -n\ln \zeta(\beta, x_{min}) -
+	\beta\sum_{i=1}^{n} \ln x_i 
 	\label{eqn:powerlaw_likelihood}
@@
     \begin{equation}
-    \mathcal{L}(\alpha, \lambda) = n*(1 - \alpha)ln\lambda - n*ln\Gamma(1 - \alpha, x_{min}\lambda) - \alpha\sum_{i=1}^{n}ln x_i - \lambda\sum_{i=1}^n x_i
+    %MRS3: I replaced ln with \ln
+    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, x_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln x_i - \lambda\sum_{i=1}^n x_i
     \end{equation}
@@
   % name candidates - correlated MSMs, Dynamical mode switching
+  % MRS3: probably not ``correlated MSMs'', that's insufficiently descriptive. Many things dynamically change modes.
+  % Maybe ``Markov state-dependent dynamics?'' You have dynamics/transport that are a function of the state, which is 
+  % determined by a Markov state model.
 
@@
 	  \centering
-	  \begin{tabular}{ll}
+          %MRS3: tweaked formatting, change back if you want!
+	  \begin{tabular}{|c|c|}
 	  \hline
@@
   % BJC2: Actually I think I prefer showing the MSD curves on one plot, like in my research journal. Since it shows shape.
+  % MRS3: OK.
   \begin{figure}
@@
 
+  %MRS3: add specific info for PRF and GAANN
+  This work was supported in part by the ACS Petroleum Research Fund grant XXXXXX and GAANN grant YYYYY.
   Molecular simulations were performed using the Extreme Science and

### 2019-09-09 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Membrane profile picture, plus other unadded figure-generation scripts

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}

\externaldocument[M-]{Draft}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thetable}{S\arabic{table}}

\title{Supporting Information: Time Series Modeling of Solute Transport in an H\textsubscript{II} 
Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

\begin{document}

  \maketitle
  \graphicspath{{./supporting_figures/}}
  \bibliographystyle{ieeetr}

  \section{Setup and analysis scripts}\label{section:python_scripts}

  All python and bash scripts used to set up systems and conduct post-simulation trajectory
  analysis are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  Documentation for the \texttt{LLC\_Membranes} repository is available at
  \texttt{https://llc-membranes.readthedocs.io/en/latest/}. Table~\ref{table:python_scripts}
  provides more detail about specific scripts used for each type of analysis performed in
  the main text.

  \begin{table}[htb!]
  \centering
  \newcolumntype{A}{ >{\centering\arraybackslash} m{2.5in} }
  \newcolumntype{B}{ >{\centering\arraybackslash} m{0.75in} }
  \newcolumntype{C}{m{2.75in}}
  \begin{tabular}{|A|B|C|}
  \hline
  \textbf{Script Name} & \textbf{Section} & ~~~~~~~~~~~~~~~~~~~~~\textbf{Description} \\
  \hline

  % mimic this
  \texttt{/setup/param.sh} & 2.1 & Parameterize liquid
  crystal monomers and solutes with GAFF \\ \hline

  \end{tabular}

  \caption{The first column provides the names of the python scripts available in
  the \texttt{LLC\_Membranes} GitHub repository that were used for system setup and
  post-simulation trajectory analysis. Paths preceding script names are relative to the
  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second columns lists the section in the main
  text where the output or usage of the script is first described. The third column
  gives a brief description of the purpose of each script.
  }~\label{table:python_scripts}

  \end{table}

  \section{Choosing a transport model}\label{section:transport_model_selection}

  We used the toolbox created by Meroz and Sokolov in order to justify our
  choice of transport model.\cite{meroz_toolbox_2015} The solutes in our systems
  exhibit anomalous transport properties characteristic of a Continuous Time
  Random Walk (CTRW).

  \subsection*{Mean Squared Displacement}

  The general form of a mean squared displacement (MSD) curve is:
  \begin{equation}
	\langle x^2(t) \rangle \sim t ^ \alpha
	\label{eqn:msd}
  \end{equation}
  For brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq
  1$, the particle of interest exhibits anomalous diffusion. Values of $\alpha$
  greater than 1 give rise to superdiffusion, while values of $\alpha$ less than
  1 give rise to subdiffusion.

  We can calculate the ensemble-averaged MSD curve by averaging the MSDs of
  each particle trajectory, where each MSD is calculated using:
  \begin{equation}
	\delta^2(t) = \| \mathbf{r}(t) - \mathbf{r}(0) \|^2
	\label{eqn:ensemble_msd}
  \end{equation}
  where $\|\cdot\|$ represents the Euclidean norm.

  The mean squared displacement of solutes in our model is a non-linear
  function of time, with $\alpha < 1$ which is indicative of anomalous
  subdiffusion. Figure \ref{fig:msd_power_law}a plots the ensemble-averaged MSD
  curve for 24 ethanol molecules diffusing in a 10 wt\% water H\textsubscript{II}
  LLC membrane system. We fit a power law of the form $Ae^{\alpha}$ to the MSD
  curve. We performed 2000 bootstrap trials by randomly sampling 24 MSD curves
  with replacement from the 24 total ethanol MSD curves. The bootstrapped average
  value of $\alpha$ is 0.75 for this system.

  \begin{figure}[!htb]
  \centering
% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -ensemble -power_law -a z -nboot 2000
% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
  \includegraphics[width=0.8\linewidth]{msd_power_law.pdf}
  \caption{(a) We fit a curve with the form of Equation~\ref{eqn:msd} to the
	  ensemble-averaged MSD curve. (b) The average value of $\alpha$, obtained using
	  fits to MSDs calculated from bootstrapped ensembles, is less than 1 suggesting
	  that ethanol molecules in our model exhibit subdiffusive
	  behavior.}\label{fig:msd_power_law}
  \end{figure}

  \subsection*{Ergodicity}

  The ergodicity of a system can help us narrow down the possible anomalous
  diffusion mechanisms. In an ergodic system, the time-averaged behavior of an
  observable should yield the same result as the ensemble average of the same
  observable. Examples of anomalous diffusion processes that are ergodic include
  random walks on fractals (RWF) and fractional brownian motion (FBM).
  Non-ergodic systems generally give rise to CTRWs with the possibility of
  combination with a RWF and/or FBM.\cite{meroz_toolbox_2015}

  We tested the ergodicity of our system by comparing the ensemble-averaged
  and time-averaged MSD curves. We calculated the MSD of each ethanol trajectory
  using Equation~\ref{eqn:ensemble_msd} and a time-averaged algorithm: 
  \begin{equation}
	\delta^2(t) = \dfrac{1}{N-t} \sum_{i=0}^{N-t-1} \| \mathbf{r}(i + t) - \mathbf{r}(i) \|^2
  \end{equation}
  where N is the total number of simulation frames, and t represents the length
  of subinterval or number of frames per subinterval. We averaged the MSD curves
  from each trajectory in order to create final MSD plots.

  The ethanol molecules exhibit non-ergodic behavior because their
  time-averaged and ensemble-averaged MSDs do not agree with each other
  (Figure~\ref{fig:ethanol_msd_comparison}). We validated our analysis using a 1
  ns simulation of a box of tip3p water molecules. As expected, since the
  particles exhibit Brownian motion, the time-averaged and ensemble-averaged MSDs
  agree with each within error (Figure~\ref{fig:water_box_msd_comparison}).

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -compare -nboot 2000 -a z
% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
  \includegraphics[width=\textwidth]{ethanol_msd_comparison.pdf}
  \caption{}\label{fig:ethanol_msd_comparison}
  \end{subfigure} 
  \begin{subfigure}{0.45\textwidth}
% Generated with msd.py -t traj_nojump.xtc -g npt.gro -r SOL -compare --fracshow 0.4 -nboot 2000 -a z
% in directory: /home/bcoscia/Documents/Gromacs/Transport/Solvent/solvent_boxes/pure_water
  \includegraphics[width=\textwidth]{water_box_msd_comparison.pdf}
  \caption{}\label{fig:water_box_msd_comparison}
  \end{subfigure} 
  \caption{(a) The time-averaged and the ensemble-averaged MSDs for ethanol in
	  an H\textsubscript{II} nanopore are not in agreement, implying non-ergodicity.
	  (b) A box of tip3p water molecules is expected to be ergodic and it is shown to
	  be true here because both MSDs are in agreement. }\label{fig:msd_comparison}
  \end{figure}

  \subsection*{Autocorrelation of steps}

% From Sokolov paper: "Assigning different waiting times τ i to each step, and assuming that the
% steps are uncorrelated as in a regular RW, gives rise to the CTRW model" -- I
% might need to check autocorrelation of steps lengths when a hop occurs rather
% than every time step. Not sure if there is enough data for that, but could check 
% a particularly hoppy trajectory after longer simulation.

  Based on the previous two sections, our model can likey be studied as a CTRW. 
  However, it is still possible that our CTRW model might also be convoluted with
  an FBM or a RWF process. In a pure CTRW, the steps are uncorrelated. 
  Both FBM and RWF exhibit anti-correlated steps.

  The steps in our system are not correlated. We showed this by calculating the
  autocorrelation function (ACF) of the step lengths in the $z$-direction. The
  ACF of a representative trajectory is shown in Figure~\ref{fig:eth_autocorrelation}.

  \begin{figure}[!htb]
  \centering
% Generated with brownian_test.py -t PR_nojump.xtc -g PR.gro -r ETH (and appropriate uncommenting -- need to rework that script)
% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
  \includegraphics[width=0.8\textwidth]{eth_autocorrelation.pdf}
  \caption{The autocorrelation function (right) of a representative ethanol
	   center of mass $z$-coordinate trajectory (left) almost immediately decays to zero,
	   indicating a complete loss of memory of it's previous position. Noise increases
	   at large time lags due to decreased sampling.}\label{fig:eth_autocorrelation}
  \end{figure}

  \clearpage
  \bibliography{transport}

\end{document}

### 2019-09-09 LLC_Membranes/llclib/physical.py

@@ -255,7 +255,6 @@ def avg_pore_loc(npores, pos, box, buffer=0, spline=False, npts=20, progress=Fal
             p_center = np.zeros([nT, npores, 2])
 
             for i in range(nT):
-                print(i)
 
                 positions = wrap_box(pos[i, ...], box[i, ...])
 

### 2019-09-11 LLC_Membranes/llclib/fitting_functions.py
Ironing out method MSDDM methodology

@@ -4,7 +4,8 @@ import numpy as np
 from scipy.stats import expon
 from LLC_Membranes.analysis import Poly_fit
 from sympy import mpmath
-from scipy.optimize import minimize
+from scipy.optimize import curve_fit, minimize
+from scipy.special import gamma
 
 
 def log_power_law(x, a, alpha):
@@ -335,3 +336,29 @@ def powerlaw_mle(x, xmin, guess=1.5):
     args = (x, xmin, True)  # (dwell times, xmin, maximize = True)
 
     return minimize(power_law_discrete_log_likelihood, guess, args=args, bounds=[(1.01, 3)]).x[0]
+
+
+def hurst_autocorrelation_flm(k, H):
+    """ Evaluate the analytical hurst autocorrelation function:
+
+    .. math::
+
+        \gamma(k) = \frac{E[L(1)^2]}{2\Gamma(2H + 1)sin(\pi H)} \times [|k-1|^{2H} - 2|k|^{2H} + |k + 1|^{2H}]
+
+    :param k: time lag values at which to calculate acf
+    :param H: hurst self-similarity parameter
+
+    :return:
+    """
+
+    autocov = np.abs(k - 1) ** (2 * H) - 2 * np.abs(k) ** (2 * H) + np.abs(k + 1) ** (2 * H)
+    autocov *= 1 / (2 * gamma(2 * H + 1) * np.sin(np.pi * H))
+
+    return autocov / autocov[0]
+
+
+def fit_hurst_autocorrelation_flm(x, max_k=-1, guess=0.5):
+
+    h_opt = curve_fit(hurst_autocorrelation_flm, np.arange(max_k + 1), x[:max_k + 1], p0=guess)[0]
+
+    return h_opt

### 2019-09-18 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Ironing out method MSDDM methodology
Justifying everything

@@
 
+  \newpage
+  \section{Estimating the Hurst Parameter}\label{section:H_estimate}
+
+  We chose to estimate the Hurst parameter, $H$ by a least squares fit to the analytical
+  autocorrelation function for fractional Brownian motion (the variance-normalized version 
+  of Equation~\ref{M-eqn:fbm_autocorrelation} in the main text):
+
+  \begin{equation}
+    \gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
+  \label{eqn:fbm_autocorrelation}
+  \end{equation}
+
+  In Figure~\ref{fig:hurst_autocorrelation}, we plotted Equation~\ref{eqn:fbm_autocorrelation}
+  for different values of $H$. When $H > 0.5$, Equation~\ref{eqn:fbm_autocorrelation} decays
+  slowly to zero meaning one needs to study large time lags with high frequency in order to
+  obtain accurate estimates. Fortunately, all of our solutes show anti-correlated motion, so
+  most of the information in Equation \ref{eqn:fbm_autocorrelation} is contained within the 
+  first few lags.
+
+  % /supporting_figures/hurst_autocorrelation.py
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{hurst_autocorrelation.pdf}
+  \caption{The analytical autocorrelation function of FBM decays to zero faster when 
+  H $<$ 0.5 compared to when H $>$ 0.5.}\label{fig:hurst_autocorrelation}
+  \end{figure}
+
+  The autocovariance function of Fractional L\'evy motion is different from fractional
+  Brownian motion (see Equation~\ref{M-eqn:fbm_autocorrelation}
+  and~\ref{M-eqn:flm_autocovariance} of the main text), but their autocorrelation 
+  structures are the same. The autocovariance function of FLM is dependent on the 
+  expected value of squared draws from the underlying L\'evy distribution, $E\big[L(1)^2\big]$. 
+  This is effectively the distribution's variance, which is undefined for most 
+  L\'evy stable distributions due to their heavy tails. As a consequence, one should 
+  expect $E\big[L(1)^2\big]$ to grow as more samples are drawn from the distribution. 
+  However, we are only interested in the autocorrelation function. In order to predict
+  the Hurst parameter from the autocorrelation function, we must show that it has 
+  well-defined structure and is independent of the coefficient in 
+  Equation~\ref{M-eqn:flm_autocovariance} of the main text. In Figure~\ref{fig:flm_autocorrelation}, 
+  we plot the average autocorrelation function from an FLM process with an increasing 
+  number of observations per generated sequence. For all simulations we set $H$=0.35 
+  and $\alpha$=1.4. The variance-normalized autocovariance function, i.e. the autocorrelation
+  function does not change with increasing sequence length. Additionally, the
+  autocorrelation function of FBM, with the same $H$ is the same.
+
+  % supporting_figures/flm_autocov.py
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{flm_autocovariance.pdf}
+  \caption{The autocorrelation function of an FLM process does not change with 
+  increasing sequence length (N). It shares the same autocorrelation function as
+  fractional Brownian motion (FBM). All sequenced used to make this plot were 
+  generated using $H$=0.35 and $\alpha$=1.4 (for FLM).}\label{fig:flm_autocovariance}
+  \end{figure}
+
+  \section{Simulating Fractional L\'evy Motion}\label{section:sFLM}
+
+  \subsection*{Achieving the right correlation structure}
+
+  We simulated FLM using the algorithm of Stoev and Taqqu~\cite{stoev_simulation_2004}.
+  There are no known exact methods for simulating FLM. As a consequence, passing a
+  value of $H$ and $\alpha$ to the algorithm does not necessarily result in the correct
+  correlation structure, although the marginal L\'evy stable distribution is correct. 
+  We applied a database-based empirical correction in order to use the
+  algorithm to achieve the correct marginal distribution and correlation structure.
+
+  Stoev and Taqqu note that the transition between negatively and positively correlated
+  draws occurs when $H = 1/ \alpha$. When $\alpha=2$, the marginal distribution is 
+  Gaussian and $H=0.5$ as expected from FBM. We corrected the input $H$ so that the 
+  value of $H$ measured based on the output sequence equaled the desired $H$. We 
+  first adjusted the value of $H$ by adding ($1 / \alpha - 0.5$), effectively 
+  recentering the correlation sign transition for any value of $1 \leq \alpha \leq 2$.
+  This correction alone does a good job for input $H$ values near 0.5, but is
+  insufficient if one desires a low values of $H$. The exact correction to $H$ is 
+  not obvious so we created a database of output $H$ values tabulated as a function
+  of input $H$ and $\alpha$ values. Figure~\ref{fig:hurst_correction} demonstrates the
+  results of applying our correction. Without the correction, FLM realizations are
+  more negatively correlated. This would result in under-predicted mean squared
+  displacements when applying the model.
+
+  % /supporting_figures/demonstrate_hurst_correction.py
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{hurst_correction.pdf}
+  \caption{Correcting the Hurst parameter input to the algorithm of Stoev and Taqqu
+  results in an FLM process with a more accurate correlation structure. We generated
+  sequences with an input $H$ of 0.35. We estimated $H$ by fitting the autocorrelation
+  function. Without the correction, $H$ is underestimated, meaning realizations are 
+  more negatively correlated than they should be.}\label{fig:hurst_correction}
+  \end{figure}
+
+  \subsection*{FLM realizations from truncated L\'evy stable distributions}
+
+  To generate realizations from an uncorrelated truncated L\'evy process, one would
+  randomly sample from the base distribution and replace values that are too large
+  with new random samples from the base distribution, repeating the process until
+  all samples are under the desired cut-off.
+
+  This procedure is complicated by the correlation structure of FLM. At a high level,
+  Stoev and Taqqu use Riemann-sum approximations of the stochastic integrals defining
+  FLM in order to generate realizations. They do this efficiently with the help of 
+  Fast Fourier Transforms. In practice, this requires one to Fourier transform a zero-padded
+  vector of random samples drawn from the appropriate L\'evy stable distribution, multiply
+  the vector in Fourier space by a kernel function and invert back to real space. The end
+  result is a correlated vector of fractional L\'evy noise.
+
+  If one is to truncate an FLM process, one can apply the simple procedure above for 
+  drawing uncorrelated values from the marginal L\'evy stable distribution, but after
+  adding correlation, the maximum drawn value is typically lower than the limit set 
+  by the user. Additionally, the shape of the distribution itself changes. Analogous
+  to the database used to correct the Hurst parameter, we created a database to 
+  correct the input truncation parameter (the maximum desired draw). The database
+  returns the value of the truncation parameter that will properly truncate the
+  output marginal distribution based on $H$, $\alpha$ and $\sigma$ (the width parameter).
+  Figure~\ref{fig:truncation_correction} shows the result of applying our correction.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{truncation_correction.pdf}
+  \caption{We can accurately truncate the marginal distribution of FLM innovations by
+  applying a correction to the input truncation parameter. We generated FLM sequences
+  and truncated the initial L\'evy stable distribution (before Fourier transforming) at 
+  a value of 0.5. After correlation structure is added, the width of the distribution 
+  of fractional L\'evy noise decreases significantly. We corrected the input truncation
+  parameter with our database resulting in a much more accurate distribution with 
+  a maximum value close to 0.5.}\label{fig:truncation_correction}
+  \end{figure}
+
   \clearpage
-  \bibliography{transport}
+  \bibliography{stochastic_transport}
 

### 2019-09-23 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Figure generation scripts + figures

@@
   \end{table}
+
+  \section{Solute Equilibration}\label{section:equilibration}
+
+  We collected all data used for model generation after the solutes were 
+  equilibrated. We assumed a solute to be equilibrated when the partition of
+  solutes in and out of the pore region stopped changing. The pore region is
+  defined as within 0.75 nm of the pore center. We've plotted the partition
+  versus time in Figure~\ref{fig:equilibration} and indicated the chosen
+  equilibration time points.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{URE_equilibration.pdf}
+  \caption{}\label{fig:URE_equilibration}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{GCL_equilibration.pdf}
+  \caption{}\label{fig:GCL_equilibration}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ACH_equilibration.pdf}
+  \caption{}\label{fig:ACH_equilibration}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{MET_equilibration.pdf}
+  \caption{}\label{fig:MET_equilibration}
+  \end{subfigure}
+  \caption{We considered a system to be equilibrated when the partition of solutes
+  between the tails and pore plateaued. Our chosen equilibration point for each
+  solute is indicated by the vertical black dashed line. (a) Urea equilibrates
+  the fastest, after 1000 ns. (b) Ethylene glycol equilibrates after 1200 ns 
+  (c) Acetic Acid does not equilibrate until 4400 ns. (d) We considered methanol
+  to be equilibrated after 3500 ns. Methanol nearly completely partitions into
+  the tails.}\label{fig:equilibration}
+  \end{figure}
 
@@
 
-  \subsection*{Autocorrelation of steps}
-
-% From Sokolov paper: "Assigning different waiting times τ i to each step, and assuming that the
-% steps are uncorrelated as in a regular RW, gives rise to the CTRW model" -- I
-% might need to check autocorrelation of steps lengths when a hop occurs rather
-% than every time step. Not sure if there is enough data for that, but could check 
-% a particularly hoppy trajectory after longer simulation.
-
-  Based on the previous two sections, our model can likey be studied as a CTRW. 
-  However, it is still possible that our CTRW model might also be convoluted with
-  an FBM or a RWF process. In a pure CTRW, the steps are uncorrelated. 
-  Both FBM and RWF exhibit anti-correlated steps.
-
-  The steps in our system are not correlated. We showed this by calculating the
-  autocorrelation function (ACF) of the step lengths in the $z$-direction. The
-  ACF of a representative trajectory is shown in Figure~\ref{fig:eth_autocorrelation}.
-
-  \begin{figure}[!htb]
-  \centering
-% Generated with brownian_test.py -t PR_nojump.xtc -g PR.gro -r ETH (and appropriate uncommenting -- need to rework that script)
-% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
-  \includegraphics[width=0.8\textwidth]{eth_autocorrelation.pdf}
-  \caption{The autocorrelation function (right) of a representative ethanol
-	   center of mass $z$-coordinate trajectory (left) almost immediately decays to zero,
-	   indicating a complete loss of memory of it's previous position. Noise increases
-	   at large time lags due to decreased sampling.}\label{fig:eth_autocorrelation}
-  \end{figure}
-
   \newpage
@@
   slowly to zero meaning one needs to study large time lags with high frequency in order to
-  obtain accurate estimates. Fortunately, all of our solutes show anti-correlated motion, so
-  most of the information in Equation \ref{eqn:fbm_autocorrelation} is contained within the 
-  first few lags.
+  accurately estimate $H$ from the data. Fortunately, all of our solutes show anti-correlated
+  motion, so most of the information in Equation \ref{eqn:fbm_autocorrelation} is contained
+  within the first few lags.
 
@@
 
-  The autocovariance function of Fractional L\'evy motion is different from fractional
-  Brownian motion (see Equation~\ref{M-eqn:fbm_autocorrelation}
+  The autocovariance function of fractional L\'evy motion is different from fractional
+  Brownian motion (see Equations~\ref{M-eqn:fbm_autocorrelation}
   and~\ref{M-eqn:flm_autocovariance} of the main text), but their autocorrelation 
@@
   L\'evy stable distributions due to their heavy tails. As a consequence, one should 
-  expect $E\big[L(1)^2\big]$ to grow as more samples are drawn from the distribution. 
+  expect $E\big[L(1)^2\big]$ to grow as more samples are drawn from the distribution
+  with the autocovariance function responding accordingly. 
   However, we are only interested in the autocorrelation function. In order to predict
   the Hurst parameter from the autocorrelation function, we must show that it has 
-  well-defined structure and is independent of the coefficient in 
+  a well-defined structure and is independent of the coefficient in 
   Equation~\ref{M-eqn:flm_autocovariance} of the main text. In Figure~\ref{fig:flm_autocorrelation}, 
@@
   and $\alpha$=1.4. The variance-normalized autocovariance function, i.e. the autocorrelation
-  function does not change with increasing sequence length. Additionally, the
-  autocorrelation function of FBM, with the same $H$ is the same.
+  function, does not change with increasing sequence length. Additionally, the
+  autocorrelation function of FBM, with the same $H$, is the same.
 
@@
   fractional Brownian motion (FBM). All sequenced used to make this plot were 
-  generated using $H$=0.35 and $\alpha$=1.4 (for FLM).}\label{fig:flm_autocovariance}
+  generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:flm_autocorrelation}
   \end{figure}
@@
 
-  \subsection*{Achieving the right correlation structure}
+  \subsection{Truncated L\'evy stable hop distributions}\label{section:truncation}
 
-  We simulated FLM using the algorithm of Stoev and Taqqu~\cite{stoev_simulation_2004}.
-  There are no known exact methods for simulating FLM. As a consequence, passing a
-  value of $H$ and $\alpha$ to the algorithm does not necessarily result in the correct
-  correlation structure, although the marginal L\'evy stable distribution is correct. 
-  We applied a database-based empirical correction in order to use the
-  algorithm to achieve the correct marginal distribution and correlation structure.
+  \textit{Determining where to truncate the hop distribution:} A pure
+  L\'evy stable distribution has heavy tails which can lead to arbitrarily
+  long hop lengths. Our distribution of hop lengths fits well to a L\'evy
+  distribution near the mean, but under samples the tails. In 
+  Figure~\ref{fig:truncation_correction} we compare the empirically 
+  measured hop length distribution of Urea to its maximum likelihood fit to
+  a L\'evy stable distribution. The ratio between the two distributions 
+  at each bin is nearly 1 close to the center, indicating a near-perfect
+  fit, larger than 1 slightly further from the center, suggesting that 
+  we slightly over sample intermediate hop lengths, and below 1 far from 
+  the center, indicating under sampling of extremely long hop lengths.
+  Based on the plot, we chose a cut-off of 0.8 nm in order to compensate for
+  over sampled intermediate hop lengths. We used the same procedure
+  to determine truncation parameters for all solutes.
 
-  Stoev and Taqqu note that the transition between negatively and positively correlated
-  draws occurs when $H = 1/ \alpha$. When $\alpha=2$, the marginal distribution is 
-  Gaussian and $H=0.5$ as expected from FBM. We corrected the input $H$ so that the 
-  value of $H$ measured based on the output sequence equaled the desired $H$. We 
-  first adjusted the value of $H$ by adding ($1 / \alpha - 0.5$), effectively 
-  recentering the correlation sign transition for any value of $1 \leq \alpha \leq 2$.
-  This correction alone does a good job for input $H$ values near 0.5, but is
-  insufficient if one desires a low values of $H$. The exact correction to $H$ is 
-  not obvious so we created a database of output $H$ values tabulated as a function
-  of input $H$ and $\alpha$ values. Figure~\ref{fig:hurst_correction} demonstrates the
-  results of applying our correction. Without the correction, FLM realizations are
-  more negatively correlated. This would result in under-predicted mean squared
-  displacements when applying the model.
-
-  % /supporting_figures/demonstrate_hurst_correction.py
   \begin{figure}
   \centering
-  \includegraphics[width=0.5\textwidth]{hurst_correction.pdf}
-  \caption{Correcting the Hurst parameter input to the algorithm of Stoev and Taqqu
-  results in an FLM process with a more accurate correlation structure. We generated
-  sequences with an input $H$ of 0.35. We estimated $H$ by fitting the autocorrelation
-  function. Without the correction, $H$ is underestimated, meaning realizations are 
-  more negatively correlated than they should be.}\label{fig:hurst_correction}
+  \includegraphics[width=0.75\textwidth]{truncation_cutoff.pdf}
+  \caption{The ratio between the empirical and maximum likelihood theoretical
+  distribution quantifies the quality of fit as function of hop length. The fit
+  is near-perfect close to the mean. Intermediate hop lengths are over sampled, 
+  and the tails are under sampled. We used this type of plot to determine the
+  appropriate place to truncate the L\'evy stable distributions.}\label{fig:truncation_cutoff}
   \end{figure}
 
-  \subsection*{FLM realizations from truncated L\'evy stable distributions}
-
+  \textit{Generating FLM realizations from a truncated L\'evy distribution:}
   To generate realizations from an uncorrelated truncated L\'evy process, one would
@@
   Figure~\ref{fig:truncation_correction} shows the result of applying our correction.
+  Note that generating this database requires a significant amount of simulation and
+  still likely doesn't perfectly correct the truncation parameter. The output leads
+  to a somewhat fuzzy cut-off of the output distribution. This is likely beneficial
+  since we observe a small proportion of hops longer the chosen truncation cut-off.
 
@@
   of fractional L\'evy noise decreases significantly. We corrected the input truncation
-  parameter with our database resulting in a much more accurate distribution with 
-  a maximum value close to 0.5.}\label{fig:truncation_correction}
+  parameter with our database resulting in a distribution close to the theoretical
+  distribution (black dashed line) with a maximum value close to 0.5.}\label{fig:truncation_correction}
+  \end{figure}
+
+  \subsection{Achieving the right correlation structure}\label{section:flm_correlation}
+
+  We simulated FLM using the algorithm of Stoev and Taqqu~\cite{stoev_simulation_2004}.
+  There are no known exact methods for simulating FLM. As a consequence, passing a
+  value of $H$ and $\alpha$ to the algorithm does not necessarily result in the correct
+  correlation structure, although the marginal L\'evy stable distribution is correct. 
+  We applied a database-based empirical correction in order to use the
+  algorithm to achieve the correct marginal distribution and correlation structure.
+
+  Stoev and Taqqu note that the transition between negatively and positively correlated
+  draws occurs when $H = 1/ \alpha$. When $\alpha=2$, the marginal distribution is 
+  Gaussian and the transition occurs at $H=0.5$ as expected from FBM. We corrected 
+  the input $H$ so that the value of $H$ measured based on the output sequence equaled
+  the desired $H$. We first adjusted the value of $H$ by adding ($1 / \alpha - 0.5$),
+  effectively recentering the correlation sign transition for any value of $1 \leq \alpha \leq 2$.
+  This correction alone does a good job for input $H$ values near 0.5, but is
+  insufficient if one desires a low value of $H$. The exact correction to $H$ is 
+  not obvious so we created a database of output $H$ values tabulated as a function
+  of input $H$ and $\alpha$ values. Figure~\ref{fig:hurst_correction} demonstrates the
+  results of applying our correction. Without the correction, FLM realizations are
+  more negatively correlated. This would result in under-predicted mean squared
+  displacements when applying the model.
+
+  % /supporting_figures/demonstrate_hurst_correction.py
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{hurst_correction.pdf}
+  \caption{Correcting the Hurst parameter input to the algorithm of Stoev and Taqqu
+  results in an FLM process with a more accurate correlation structure. We generated
+  sequences with an input $H$ of 0.35. We estimated $H$ by fitting the autocorrelation
+  function. Without the correction, $H$ is underestimated, meaning realizations are 
+  more negatively correlated than they should be.}\label{fig:hurst_correction}
   \end{figure}

### 2019-09-23 LLC_Membranes/analysis/sfbm_parameters.py

@@ -141,6 +141,7 @@ class SFBMParameters(object):
         self.hop_series_order = [[] for _ in range(self.nres)]
         self.nsolute = self.com.shape[1]
         self.transition_matrix = np.zeros([self.nmodes, self.nmodes])
+        self.count_matrix = np.zeros_like(self.transition_matrix)
         self.dwell_lower_limit = []
         self.max_hop = 0  # The maximum hop length
 
@@ -826,16 +827,16 @@ class SFBMParameters(object):
 
         nT = self.partition.shape[0]
 
-        count_matrix = np.zeros_like(self.transition_matrix, dtype=int)
+        self.count_matrix = np.zeros_like(self.transition_matrix, dtype=int)
 
         for t in range(start, nT):  # start at frame 1. May need to truncate more as equilibration
             transitioned_from = self.partition[t - 1, :].astype(int)
             transitioned_to = self.partition[t, :].astype(int)
             for pair in zip(transitioned_from, transitioned_to):
-                count_matrix[pair[0], pair[1]] += 1
+                self.count_matrix[pair[0], pair[1]] += 1
 
         # normalize so rows sum to unity
-        self.transition_matrix = (count_matrix.T / count_matrix.sum(axis=1)).T
+        self.transition_matrix = (self.count_matrix.T / self.count_matrix.sum(axis=1)).T
 
     def update_database(self, file="msd.db", tablename="msd", type='parameters', data=None):
         """ Update SQL database with information from this run

### 2019-09-30 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Draft revisions + additions

@@
 
-  \section{Choosing a transport model}\label{section:transport_model_selection}
-
-  We used the toolbox created by Meroz and Sokolov in order to justify our
-  choice of transport model.\cite{meroz_toolbox_2015} The solutes in our systems
-  exhibit anomalous transport properties characteristic of a Continuous Time
-  Random Walk (CTRW).
-
-  \subsection*{Mean Squared Displacement}
-
-  The general form of a mean squared displacement (MSD) curve is:
-  \begin{equation}
-	\langle x^2(t) \rangle \sim t ^ \alpha
-	\label{eqn:msd}
-  \end{equation}
-  For brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq
-  1$, the particle of interest exhibits anomalous diffusion. Values of $\alpha$
-  greater than 1 give rise to superdiffusion, while values of $\alpha$ less than
-  1 give rise to subdiffusion.
-
-  We can calculate the ensemble-averaged MSD curve by averaging the MSDs of
-  each particle trajectory, where each MSD is calculated using:
-  \begin{equation}
-	\delta^2(t) = \| \mathbf{r}(t) - \mathbf{r}(0) \|^2
-	\label{eqn:ensemble_msd}
-  \end{equation}
-  where $\|\cdot\|$ represents the Euclidean norm.
-
-  The mean squared displacement of solutes in our model is a non-linear
-  function of time, with $\alpha < 1$ which is indicative of anomalous
-  subdiffusion. Figure \ref{fig:msd_power_law}a plots the ensemble-averaged MSD
-  curve for 24 ethanol molecules diffusing in a 10 wt\% water H\textsubscript{II}
-  LLC membrane system. We fit a power law of the form $Ae^{\alpha}$ to the MSD
-  curve. We performed 2000 bootstrap trials by randomly sampling 24 MSD curves
-  with replacement from the 24 total ethanol MSD curves. The bootstrapped average
-  value of $\alpha$ is 0.75 for this system.
-
-  \begin{figure}[!htb]
-  \centering
-% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -ensemble -power_law -a z -nboot 2000
-% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
-  \includegraphics[width=0.8\linewidth]{msd_power_law.pdf}
-  \caption{(a) We fit a curve with the form of Equation~\ref{eqn:msd} to the
-	  ensemble-averaged MSD curve. (b) The average value of $\alpha$, obtained using
-	  fits to MSDs calculated from bootstrapped ensembles, is less than 1 suggesting
-	  that ethanol molecules in our model exhibit subdiffusive
-	  behavior.}\label{fig:msd_power_law}
-  \end{figure}
-
-  \subsection*{Ergodicity}
-
-  The ergodicity of a system can help us narrow down the possible anomalous
-  diffusion mechanisms. In an ergodic system, the time-averaged behavior of an
-  observable should yield the same result as the ensemble average of the same
-  observable. Examples of anomalous diffusion processes that are ergodic include
-  random walks on fractals (RWF) and fractional brownian motion (FBM).
-  Non-ergodic systems generally give rise to CTRWs with the possibility of
-  combination with a RWF and/or FBM.\cite{meroz_toolbox_2015}
-
-  We tested the ergodicity of our system by comparing the ensemble-averaged
-  and time-averaged MSD curves. We calculated the MSD of each ethanol trajectory
-  using Equation~\ref{eqn:ensemble_msd} and a time-averaged algorithm: 
-  \begin{equation}
-	\delta^2(t) = \dfrac{1}{N-t} \sum_{i=0}^{N-t-1} \| \mathbf{r}(i + t) - \mathbf{r}(i) \|^2
-  \end{equation}
-  where N is the total number of simulation frames, and t represents the length
-  of subinterval or number of frames per subinterval. We averaged the MSD curves
-  from each trajectory in order to create final MSD plots.
-
-  The ethanol molecules exhibit non-ergodic behavior because their
-  time-averaged and ensemble-averaged MSDs do not agree with each other
-  (Figure~\ref{fig:ethanol_msd_comparison}). We validated our analysis using a 1
-  ns simulation of a box of tip3p water molecules. As expected, since the
-  particles exhibit Brownian motion, the time-averaged and ensemble-averaged MSDs
-  agree with each within error (Figure~\ref{fig:water_box_msd_comparison}).
-
-  \begin{figure}[!htb]
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -compare -nboot 2000 -a z
-% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
-  \includegraphics[width=\textwidth]{ethanol_msd_comparison.pdf}
-  \caption{}\label{fig:ethanol_msd_comparison}
-  \end{subfigure} 
-  \begin{subfigure}{0.45\textwidth}
-% Generated with msd.py -t traj_nojump.xtc -g npt.gro -r SOL -compare --fracshow 0.4 -nboot 2000 -a z
-% in directory: /home/bcoscia/Documents/Gromacs/Transport/Solvent/solvent_boxes/pure_water
-  \includegraphics[width=\textwidth]{water_box_msd_comparison.pdf}
-  \caption{}\label{fig:water_box_msd_comparison}
-  \end{subfigure} 
-  \caption{(a) The time-averaged and the ensemble-averaged MSDs for ethanol in
-	  an H\textsubscript{II} nanopore are not in agreement, implying non-ergodicity.
-	  (b) A box of tip3p water molecules is expected to be ergodic and it is shown to
-	  be true here because both MSDs are in agreement. }\label{fig:msd_comparison}
-  \end{figure}
+%  \section{Choosing a transport model}\label{section:transport_model_selection}
+%
+%  We used the toolbox created by Meroz and Sokolov in order to justify our
+%  choice of transport model.\cite{meroz_toolbox_2015} The solutes in our systems
+%  exhibit anomalous transport properties characteristic of a Continuous Time
+%  Random Walk (CTRW). 
+%
+%  \subsection*{Mean Squared Displacement}
+%
+%  The general form of a mean squared displacement (MSD) curve is:
+%  \begin{equation}
+%	\langle x^2(t) \rangle \sim t ^ \alpha
+%	\label{eqn:msd}
+%  \end{equation}
+%  For brownian motion, $\alpha = 1$ and the MSD is linear. When $\alpha \neq
+%  1$, the particle of interest exhibits anomalous diffusion. Values of $\alpha$
+%  greater than 1 give rise to superdiffusion, while values of $\alpha$ less than
+%  1 give rise to subdiffusion.
+%
+%  We can calculate the ensemble-averaged MSD curve by averaging the MSDs of
+%  each particle trajectory, where each MSD is calculated using:
+%  \begin{equation}
+%	\delta^2(t) = \| \mathbf{r}(t) - \mathbf{r}(0) \|^2
+%	\label{eqn:ensemble_msd}
+%  \end{equation}
+%  where $\|\cdot\|$ represents the Euclidean norm. 
+%
+%  The mean squared displacement of solutes in our model is a non-linear
+%  function of time, with $\alpha < 1$ which is indicative of anomalous
+%  subdiffusion. Figure \ref{fig:msd_power_law}a plots the ensemble-averaged MSD
+%  curve for 24 ethanol molecules diffusing in a 10 wt\% water H\textsubscript{II}
+%  LLC membrane system. We fit a power law of the form $Ae^{\alpha}$ to the MSD
+%  curve. We performed 2000 bootstrap trials by randomly sampling 24 MSD curves
+%  with replacement from the 24 total ethanol MSD curves. The bootstrapped average
+%  value of $\alpha$ is 0.75 for this system. 
+% 
+%  \begin{figure}[!htb]
+%  \centering
+%% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -ensemble -power_law -a z -nboot 2000
+%% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
+%  \includegraphics[width=0.8\linewidth]{msd_power_law.pdf}
+%  \caption{(a) We fit a curve with the form of Equation~\ref{eqn:msd} to the
+%	  ensemble-averaged MSD curve. (b) The average value of $\alpha$, obtained using
+%	  fits to MSDs calculated from bootstrapped ensembles, is less than 1 suggesting
+%	  that ethanol molecules in our model exhibit subdiffusive
+%	  behavior.}\label{fig:msd_power_law}
+%  \end{figure}
+%
+%  \subsection*{Ergodicity}
+%
+%  The ergodicity of a system can help us narrow down the possible anomalous
+%  diffusion mechanisms. In an ergodic system, the time-averaged behavior of an
+%  observable should yield the same result as the ensemble average of the same
+%  observable. Examples of anomalous diffusion processes that are ergodic include
+%  random walks on fractals (RWF) and fractional brownian motion (FBM).
+%  Non-ergodic systems generally give rise to CTRWs with the possibility of
+%  combination with a RWF and/or FBM.\cite{meroz_toolbox_2015} 
+%
+%  We tested the ergodicity of our system by comparing the ensemble-averaged
+%  and time-averaged MSD curves. We calculated the MSD of each ethanol trajectory
+%  using Equation~\ref{eqn:ensemble_msd} and a time-averaged algorithm: 
+%  \begin{equation}
+%	\delta^2(t) = \dfrac{1}{N-t} \sum_{i=0}^{N-t-1} \| \mathbf{r}(i + t) - \mathbf{r}(i) \|^2
+%  \end{equation}
+%  where N is the total number of simulation frames, and t represents the length
+%  of subinterval or number of frames per subinterval. We averaged the MSD curves
+%  from each trajectory in order to create final MSD plots.
+%
+%  The ethanol molecules exhibit non-ergodic behavior because their
+%  time-averaged and ensemble-averaged MSDs do not agree with each other
+%  (Figure~\ref{fig:ethanol_msd_comparison}). We validated our analysis using a 1
+%  ns simulation of a box of tip3p water molecules. As expected, since the
+%  particles exhibit Brownian motion, the time-averaged and ensemble-averaged MSDs
+%  agree with each within error (Figure~\ref{fig:water_box_msd_comparison}).
+%
+%  \begin{figure}[!htb]
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%% Generated with : msd.py -t PR_nojump.xtc -g PR.gro -r ETH -compare -nboot 2000 -a z
+%% in directory: /home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/ETH/10wt
+%  \includegraphics[width=\textwidth]{ethanol_msd_comparison.pdf}
+%  \caption{}\label{fig:ethanol_msd_comparison}
+%  \end{subfigure} 
+%  \begin{subfigure}{0.45\textwidth}
+%% Generated with msd.py -t traj_nojump.xtc -g npt.gro -r SOL -compare --fracshow 0.4 -nboot 2000 -a z
+%% in directory: /home/bcoscia/Documents/Gromacs/Transport/Solvent/solvent_boxes/pure_water
+%  \includegraphics[width=\textwidth]{water_box_msd_comparison.pdf}
+%  \caption{}\label{fig:water_box_msd_comparison}
+%  \end{subfigure} 
+%  \caption{(a) The time-averaged and the ensemble-averaged MSDs for ethanol in
+%	  an H\textsubscript{II} nanopore are not in agreement, implying non-ergodicity.
+%	  (b) A box of tip3p water molecules is expected to be ergodic and it is shown to
+%	  be true here because both MSDs are in agreement. }\label{fig:msd_comparison}
+%  \end{figure}
 
@@
   Figure~\ref{fig:truncation_correction} we compare the empirically 
-  measured hop length distribution of Urea to its maximum likelihood fit to
+  measured transition emission distribution of the MSDDM for Urea to its maximum likelihood fit to
   a L\'evy stable distribution. The ratio between the two distributions 
@@
   still likely doesn't perfectly correct the truncation parameter. The output leads
-  to a somewhat fuzzy cut-off of the output distribution. This is likely beneficial
-  since we observe a small proportion of hops longer the chosen truncation cut-off.
+  to a somewhat fuzzy, rather than abrupt, cut-off of the output distribution. This 
+  is likely beneficial since we observe a small proportion of hops longer the chosen
+  truncation cut-off. When the cut-off value is close to the L\'evy stable $\sigma$ parameter,
+  as it is in our anomalous diffusion models, we observed that the tails of the 
+  truncated distribution tend to be undersampled. In order to maintain the distribution's 
+  approximate shape up to the cut-off value we recommend ensuring that the cut-off
+  value is at least 2 times $\sigma$. However, this may lead to a slight over-prediction
+  of the MSD.
 
@@
 
+  \section{2-state MSDDM parameters}\label{section:simple_msddm_params}
+
+  We used a simple 2-state model to illustrate how the self-transition probability 
+  effects simulated MSDs generated from the MSDDM. We used the following parameters:
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{|c|c|c|c|}
+  \hline
+  State & H     & $\alpha_h$ & $\sigma$ \\\hline
+  1     & 0.1  & 1.7       & 0.04    \\
+  2     & 0.2  & 1.5       & 0.04    \\
+  T     & 0.4  & 1.4       & 0.04    \\\hline
+  \end{tabular}
+  \caption{Values of $H$, $\alpha_h$ and $\sigma$ used to simulate realizations
+  of the simple MSDDM whose MSDs are shown in Figure~\ref{M-fig:T_sensitivity} of
+  the main text. The values are chosen to be similar to those in Table~\ref{M-table:msddm_params}
+  of the main text.}\label{table:msddm_params}
+  \end{table}
+
   \clearpage

### 2019-10-01 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
New figures and finished first draft

@@
 
+  \section{Verifying Markovianity}\label{section:markov_validation}
+
+  We verified the Markovianity of our transition matrix, $T$, in two ways. First we 
+  ensured that the process satisfied detailed balance:
+  \begin{equation}
+  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
+  \end{equation}
+  where $P$ is the equilibrium distribution of states. This implies that the number
+  of transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. Graphical 
+  representations of the count matrices show that this is true in Figure~\ref{fig:counts}.
+
+  Second, we ensured that the transition matrix did not change on coarser time scales.
+  In Figures~\ref{fig:counts} and~\ref{fig:transitions}, we show that increasing the 
+  length of time between samples does not change the properties of the count or
+  probability transition matrices.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{URE_counts.pdf}
+  \caption{Urea}\label{fig:URE_counts}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{GCL_counts.pdf}
+  \caption{Ethylene Glycol}\label{fig:GCL_counts}
+  \end{subfigure}
+  \caption{The number of transitions from state $i$ to $j$ and $j$ to $i$ are very close
+  indicating that our process obeys detailed balance. Detailed balance is conserved for 
+  different sized time steps.}\label{fig:counts}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{URE_transitions.pdf}
+  \caption{Urea}\label{fig:URE_transitions}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{GCL_transitions.pdf}
+  \caption{Ethylene Glycol}\label{fig:GCL_transitions}
+  \end{subfigure}
+  \caption{As the timestep between observations increases, the probability
+  transition matrix does not change signficantly.}\label{fig:transitions}
+  \end{figure}
+
   \section{2-state MSDDM parameters}\label{section:simple_msddm_params}

### 2019-10-01 Ben_Manuscripts/stochastic_transport/Draft.tex
Added draft

\documentclass{article}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

\externaldocument[S-]{Supporting_Information}

\title{Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
\author{Benjamin J. Coscia \and Michael R. Shirts}

\begin{document}

  \graphicspath{{./figures/}}
  \maketitle

  \begin{abstract}

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories, in order
  to predict solute mean squared displacements (MSDs). With our first model, based
  on the anomalous diffusion literature, we show how solute dynamics can be modeled as
  a fractional diffusion process subordinate to a continuous time random walk.
  We parameterize the distribution of dwell times, hop lengths between dwells and
  correlation between hops. We explore 2 variations of the model. The first variation
  applies a single set of parameters to the solutes and the second applies 2 sets
  of parameters based on the solute's radial distance from the closest pore center.
  Our second model, an adaptation of Markov state models, treats the system
  as a Markov process where we quantify the transitions between a set of 
  explicitly defined states. We incorporate the magnitude and temporal correlation
  of positional fluctuations into each state and transitions between states to gain
  further insight and allow us to predict solute MSDs. We show that our models 
  reasonably reproduce MSDs calculated from molecular simulations. The anomalous 
  diffusion shows superior predictive performance, in many cases exactly reproducing
  MD results within error. We use the parameters of each model to offer additional mechanistic
  insight. These parameters are important for identifying specific differences in 
  solute transport behavior. The differences suggest modifications that can be
  made to LLC membrane monomers in order to increase or reduce selectivity towards a 
  specific solute.

  \end{abstract}

  \section{Introduction}

  % MRS1: I would start with something more central to the content of the paper - how do solutes move in complex separations membranes?  Let people know right from the start what the paper is about.  This paragraph should still be in the intro, but start with something that captures the main question of the paper. 
  % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
  % BJC2: I'm not sure if this is exactly what you meant though
%  Making sense of solute motion in complex separations membranes is central to 
%  understanding transport mechanisms and formulating membrane design principles.
  % MRS3: seems pretty good.  We can tweak later when turning into text; I don't think that it will really affect the logic of the paper. The introduction will be important here to set the stage, but probably more of that will be in the next paragraph.

  Mathematical descriptions of transport in complex separations membranes are a powerful 
  way to understand mechanisms and formulate membrane design principles. The complexity
  of a model generally parallels the complexity of the transport mechanism at hand, as
  well as the desired outputs. In dense homogeneous membranes, the solution-diffusion 
  model can extract diffusion and partition coefficients and has successfully predicted
  solute transport rates. Analogously, pore-flow models yield predictions of diffusion 
  coefficients and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
  Modern single particle tracking approaches take us beyond continuum modeling and 
  allow us to characterize complex diffusive behavior.~\cite{manzo_review_2015} 
  At the molecular level, one can use molecular dynamics (MD) simulations to study both
  single particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate speculation on the molecular origins of separations
  by attempting to give a more intuitive understanding of how solutes move as a function
  of their environment, in turn suggesting experiments that should be run.

  % BJC1: tie this paragraph into above by commenting that highly selective membranes
  % often have complex mechanistic reasons that aren't explained by simpler models
  % BJC3:maybe change this paragraph to just be examples of highly selective separations, not
  Facile design of highly selective separations membranes is desirable in numerous
  applications. The ability to efficiently separate ions from saline water sources using 
  membranes has been actively pursued for years in an effort to create potable water for 
  people in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable barriers to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
  The speed at which we achieve these or any other selective separation will be 
  heavily influenced by the quality of insights gained by the modeling approaches above.

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  LLC membranes have the potential to disrupt conventional membrane separation techniques by 
  being selective based not only on size and charge, but on solute chemical functionality
  as well.~\cite{dischinger_application_2017} One can tune the functionality of LLC monomers
  in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two types of LLC membranes are in active development. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability, it is considerably
  easier to synthesize.

%  Regardless of which LLC phase ones studies, one must contend with the large chemical design
%  space available to design these types of membranes. 
  We want to use a molecular model in order to understand how we can leverage the large 
  chemical space available for LLC monomer design in order to create efficient solute-specific
  separations. To date, only a limited subset of LLC monomers have been studied in membrane
  applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, there have been shown selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling provides the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms allowing us to move beyond 
  traditional Edisonian design.

  In our previous work, we used molecular dynamics (MD) simulations to study the transport
  of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
  %BJC3: not sure the following sentence needs to be said.
  The H\textsubscript{II} is a simpler geometry to model than the Q\textsubscript{I} phase.  
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

  In this work, we use the output of our MD simulations to construct two new classes of 
  mathematical models which can predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
  of these models requires a dive into stochastically driven processes.

%  Our approach employs descriptive stochastic models that sufficiently
%  capture solute dynamics are capable of projecting long timescale transport behavior in addition to gaining a deeper understanding
%  of solute behavior on short timescales. In this work we explore two types of stochastic
%  models parameterized by our MD simulations.
%  
%  Unfortunately, the timescales that we can simulate with MD are insufficient to be
%  able to make well-converged predictions of macroscopic transport properties 
%  traditionally used to characterize membranes in the lab.
%  \begin{itemize}
%    \item However, if we use descriptive stochastic models that sufficiently capture solute
%    dynamics, then we could project long timescale behavior in addition to gaining
%    a deeper understanding of solute behavior on short timescales.
%  \end{itemize}

  Researchers have developed a rigorous theoretical foundation for describing the 
  motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
  The tools introduced by fractional calculus are instrumental to this theory. They
  allow us to generalize the normally linear diffusion equation to fractional
  derivative orders, providing descriptions of a much more diverse set of behavior.~\cite{klages_anomalous_2008}

  Three well-known classes of behavior leading to anomalous subdiffusion are 
  continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  The theory is frequently used to describe single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
  A CTRW is characterized by a distribution of hop lengths and dwell times, 
  where each each hop is characterized by independent random draws from 
  each distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways 
  and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
  These processes can occur alone or in combination.

% BJC3: omitted because too rigid. Ergodicity is hard to prove with 24 solute trajectories.
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.7\textwidth]{subdiffusion_decision_tree.pdf}
%  \caption{This decision tree, adapted from Meroz and Sokolov~\cite{meroz_toolbox_2015},
%  can be used to isolate potential subdiffusive transport mechanisms based on 
%  single solute trajectories.}\label{fig:decision_tree}
%  \end{figure}

  % BJC2: moved this from below
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. We fit anomalous diffusion models in two ways: First, based 
  on a single set of parameters. Second, we use a two-state approach incorporating
  two sets of parameters based on a solute's radial distance from the closest pore center.

  While elegant, pure anomalous diffusion theory may in some cases give only a 
  qualitative understanding of transport mechanisms. Complex temporal relationships in 
  between hops may have a significant effect on the average MSD. Inhomogeneity of 
  a medium or multiple types of interactions may lead to a number of distinct 
  diffusive regimes. In this case, a state based model may be useful.

%  \noindent We can use the observations of transport from our previous work in order to create 
%  state-based models.
%  \begin{itemize}
%  	\item We know that dynamics differ between solutes moving inside the pores and 
%  	in the tails.
%  	\item We can use the anomalous diffusion approach to model our data as a 
%  	function of radial distance from the closest pore center.
%  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
%  	methods of Markov state modeling.
%  \end{itemize}

  % moved parts of method to here.
  Markov state models (MSMs) are a popular class of models used to project long timescale
  system properties based on molecular simulation trajectories by identifying
  different dynamical modes and quantifying the rates of transitions between them.
  MSMs are frequently used to study systems with slow dynamics, such as protein 
  folding.~\cite{snow_how_2005,chodera_automatic_2007} Researchers typically aim to 
  come up with a low dimensional representation of the system based on features 
  which preserve the process kinetics. This still often results in hundreds to thousands
  of distinct states.~\cite{chodera_markov_2014}

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three observed solute trapping mechanisms.
  Standard MSMs assume first order kinetics and are typically applied 
  towards determining equilibrium populations of and the transitions between 
  various state configurations.~\cite{bowman_using_2009} We extend the framework
  to include dynamics within states and between jumps. That is we parameterize 
  and incorporate into our model the magnitude and temporal correlation of
  fluctuations in solute position while in each state as well as during transitions
  to different states. 
  %Temporal correlation in position has a significant influence on 
  %a solute's mean squared displacement.

  In this work we apply the two modeling approaches in order to predict the long
  timescale behavior of the four fastest moving solutes studied in our previous work.
  Specifically, we study methanol, urea, ethylene glycol and acetic acid. In addition
  to moving quickly, allowing them to extensively explore membrane structural space,
  these solutes have a range of chemical functionality and experience each of the 
  three trapping mechanisms to different degrees. It is our goal to reproduce
  the mean squared displacements (MSDs) exhibited by each solute on MD timescales and
  then to project the long-term dynamics of each solute. We can gain further
  mechanistic insight by studying the parameters of each model. 
  %BJC3: need to decide value in long term projections

%  If we can reproduce the MD MSDs within reason
%  then we can use the parameters of our model to gain additional mechanistic insight.
%  
      %MRS: do the solutes also have some diversity of mechanisms (that were observed previously?)
    %BJC1: Yes. Need to put following into words
    %BJC1: Ranking of time spent in pore region: AcOH > EG > URE > MeOH  (spans 4th most to 3rd least)
    %BJC1: All have high hop frequency which is consistent with fast motion
    %BJC1: Hbonding: Urea barely hbonds. AcOH and EG hbond a lot. AcOH has highest hbond lifetime of all 20 solutes. MeOH on par with all other simple alcohols
    %BJC1: Sodium Association: Urea coordinates with sodium the most of all 20 solutes. AcOH, EG, MeOH spread out of rest of range. Lifetime similar

  \section{Methods}

  We ran all MD simulations and energy minimizations using GROMACS 2018. 
  ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
  We performed all post-simulation trajectory analysis using python scripts which 
  are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  The appropriate scripts to use for subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information.

  \subsection{Molecular Dynamics Simulations}

  We studied transport of solutes in the H\textsubscript{II} phase using an atomistic
  molecular model of four pores in a monoclinic unit cell with 10 \% water by weight 
  (see Figure~\ref{fig:membrane_structure}). Approximately one third of the water 
  molecules occupy the tail region with the rest near the pore center. We chose to
  focus our study on the 10 wt \% water system because solutes move significantly 
  faster than in the 5 wt \% system studied previously. Appropriate stochastic 
  modeling requires that solutes sample the accessible mechanisms with representative
  probability.

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the distal tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  \end{figure}

  We chose to study a subset of the 4 fastest moving solutes from our previous
  work: methanol, acetic acid, urea and ethylene glycol. For each solute we 
  created a separate system and to each system we added 6 solutes per pore 
  for a total of 24 solutes. This number of solutes per pore provides a balance
  of a low degree of interaction between solutes, since we are primarily interested 
  in solute-membrane interactions at present, as well as a sufficient amount of 
  data from which to generate statistics on the time scales which we simulate.
  Further details on the setup and equilibration of these systems are described in
  our previous work.\cite{coscia_chemically_2019}

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data. We simulated the system with a time step of 2 fs at a pressure
  of 1 bar and 300 K controlled by the Parinello-Rahman barostat and the v-rescale 
  thermostat respectively. We recorded frames every 0.5 ns.

  We considered each system to be equilibrated when the solute partition between the 
  pore and tail region stopped changing. We excluded data collected before equilibration
  from our analysis. We plotted the solute partition versus time in Figure~\ref{S-fig:equilibration}
  of the Supporting Information in order to justify our choice of equilibration times
  for each solute.

  \subsection{The Anomalous Diffusion Model}\label{method:model_sFBM}

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle x^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. A value of $\alpha_d < 1$ indicates a subdiffusive process, 
  while values of $\alpha_d = 1$ and $\alpha_d > 0$ are characteristic of Brownian and
  superdiffusive motion respectively.

  %MRS: describe the physical situations in which one would want to choose each of these ways of calculating the MSD.
  %BJC1: For determining ergodicity. Ensemble for determining anomalous exponent. Not sure I'll use ensemble MSD

%  We analyzed both the ensemble-averaged and time-averaged MSDs of the simulated
%  trajectories. The ensemble-averaged MSD measures the displacement of a particle 
%  from its initial position~\cite{meroz_toolbox_2015} and can be written as
%  \begin{equation}
%  \langle x^2(t) \rangle = \langle x(t) - x(0) \rangle^2
%  \label{eqn:ensemble_msd}
%  \end{equation}
%%	\item The average MSD calculated in this way recovers the form of
%%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
%  The time-averaged MSD eliminates initial position dependence by measuring all
%  possible displacements over time lag $\tau$ and can be written as:
%  \begin{equation}
%  \overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
%  \end{equation}
%  where T is the length of the trajectory~\cite{meroz_toolbox_2015}.

  %BJC3: removed ensemble MSD because it's not used
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. If the underlying 
  subdiffusive process is not ergodic, like a pure CTRW, the time averaged MSD becomes
  linear.~\cite{meroz_toolbox_2015}

%  We determined the ergodicity of the solute trajectories using the ergodicity breaking
%  parameter~\cite{cherstvy_anomalous_2013}:
%  %First, we tested whether the increments of the process were stationary using the augmented Dickey-Fuller test.
%  \begin{equation}
%  EB = \lim_{T \to \infty} \frac{\bigg(\bigg\langle \overline{x^2(T)}^2 \bigg\rangle - \bigg\langle \overline{x^2(T)} \bigg\rangle^2\bigg)}{\bigg\langle \overline{x^2(T)} \bigg\rangle^2}
%  \end{equation}
%  Simply stated, $EB$ quantifies the variance or heterogeneity in the time averaged
%  MSD generated from independent trajectories after ample time has passed. For 
%  ergodic systems, $EB=0$.

  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
  % MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
  % BJC1: modified this paragraph to parallel the flow chart. I'm still not sure the
  % best place for this. It seems like it belongs in the discussion, but I need to 
  % justify the choice in model so I can write the methods about the chosen models
  % BJC2: Perhaps just say that we think it's sFBM and move the proof to discussion.
  \subsubsection*{Subordinated Fractional Brownian Motion}

  We believe that solute motion in the system studied here may be consistent with 
  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
  the leading process is a CTRW. We observe hopping and trapping which is consistent
  with a CTRW along with negatively correlated hops which is consistent with FBM.

  One can characterize a CTRW process using the parameters which describe its dwell 
  time and hop length distributions. We used the \texttt{ruptures} python package in 
  order to automatically identify mean shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018} 
  We used the corresponding hop lengths and dwell times between hops to construct 
  empirical distributions.

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha_d}$.~\cite{meroz_toolbox_2015}
  %BJC3: is it okay to leave above equation in line? Or should it get numbered?
  %BJC3: I added subscript d to the dwell time alpha because alpha is a standard parameter for power laws and levy stable distributions
% BJC3: following includes normalization constant 
%  of the form:
%  \begin{equation}
%  (\beta - 1)x_{min}^{\beta - 1}x^{-\beta}
%  \end{equation}  
%  where $\beta = (1 + \alpha)$ and $x_{min}$ is the smallest measured value of $x_i$.~\cite{meroz_toolbox_2015,clauset_power-law_2009}
%  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete values dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha_d$ 
  parameter we calculated by maximizing the following likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha_d$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. We can not
  observe dwell times longer than the length of a single trajectory. 
  % Could be an interesting factoid, but not necessary 
  % In fact, the longest dwell time observed by any solute in this study is X. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we may need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha_d}e^{-\lambda t}$.
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha_d$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha_d, \lambda) = n(1 - \alpha_d)\ln\lambda - n\ln\Gamma(1 - \alpha_d, t_{min}\lambda) - \alpha_d\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

  \textit{Correlated hop length distributions:} The marginal distribution of hops by solutes 
  undergoing an sFBM process is Gaussian, therefore we parameterize it by its standard deviation, 
  $\sigma$.~\cite{metzler_random_2000, metzler_anomalous_2014,neusius_subdiffusion_2009}
  The measured mean is always very close to zero so we assume that it is exactly zero
  in our time series simulations since we have no reason to expect drift in either direction.

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies correlated hops which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 lags of the empirically measured
  autocorrelation function.

  \subsubsection*{Subordinated Fractional L\'evy Motion}

  If the distribution of hops is not Gaussian, we can model them with the
  more general class of L\'evy stable distributions. For independent and identically
  distributed random variables, the generalized central limit theorem assures 
  convergence of the associated probability distribution function (PDF) to a 
  L\'evy stable PDF. \cite{klages_anomalous_2008} The characteristic equation which 
  describes the Fourier transform of a L\'evy stable PDF is:
  \begin{equation}
    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
  \end{equation}
  where \\
  \[\omega(k, \alpha_h) = \begin{cases}
  	\tan{\frac{\pi \alpha_h}{2}} & \text{if}~\alpha_h \neq 1, 0 < \alpha_h < 2, \\
  	-\frac{2}{\pi}\ln |k| & \text{if}~\alpha_h = 1
  	 \end{cases}
  \]
  $\alpha_h$ is the index of stability or L\'evy index, $\beta$ is the skewness 
  parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter. The most
  familiar case, and 1 of 3 that can be expressed in terms of elementary functions,
  is the Gaussian PDF ($\alpha_h$ = 2, $\beta$ = 0). We assume symmetric distributions
  centered about 0 implying that $\beta$ and $\mu$ are both 0.

  Assuming hops are correlated, solute behavior may be described by subordinated 
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to describe
  hop correlations because they share the same autocorrelation structure.~\cite{tikanmaki_fractional_2010}
  The autocovariance function for FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
  simulations illustrating this point.  % BJC3: could use another reference proving mathematically what I show numerically

  Analogous to power law dwell times, the heavy tails of L\'evy stable 
  hop length distributions result in rare but arbitrarily long hops. These long
  and unrealistic hops result in over-estimated simulated MSDs. We observe that
  the distribution of hops observed in our MD simulations are well approximated 
  by L\'evy stable distributions close to the mean, but they significantly under-sample
  the tails. We chose to truncate the L\'evy stable distributions based
  on where the theoretical probability distribution function (PDF) starts to 
  deviate from the empirically measured PDF (see Section~\ref{S-section:truncation}
  of the Supporting Information).

  % BJC3: maybe a table of cut-offs used here. We will see how close they are. Might
  % use the same for all.

  \subsubsection*{Multiple Dynamical Modes}

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

  % BJC3: A small figure describing above might be useful, or maybe point to a figure in supporting info

  For the two mode model, we defined a transition matrix describing the rate at
  which solutes moved between the tail and pore region. To do so, we populated a
  2$\times$2 count matrix by incrementing the appropriate entry by 1 each time step. 
  For example, if we observed the solute in the tails followed by a transition to 
  the pores, we incremented the $(2, 1)$ entry of the count matrix by 1. We generated
  the transition probability matrix from the count matrix by normalizing the 
  entries in each row so that they summed to unity.

  \subsubsection*{Simulating Anomalous Diffusion}

  We simulated models with all combinations of dwell and hop length distributions
  described above, summarized in Table~\ref{table:anomalous_models}. All models 
  include correlation between hops.
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{|c|c|c|}
	  \hline
	  Dwell Distribution                & Hop Length Distribution & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
	  \end{tabular}
	  \caption{We tested models with various modifications to the dwell and hop
	  length distributions. We incorporate correlation structure into all models.}\label{table:anomalous_models}
 \end{table}

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10000 anomalous diffusion trajectories of length $T_{sim}$ in
  order to directly compare our model's predictions to MD simulations. $T_{sim}$ varied due to
  differing solute equilibration times. We constructed trajectories by simulating 
  sequences of dwell times and correlated hop lengths generated based on
  parameters randomly chosen from our bootstrapped parameter distributions. We 
  propagated each trajectory until the total time equaled or exceeded $T_{sim}~ \mu$s, then
  truncated the last data point so that the total time exactly equaled $T_{sim}~ \mu$s since
  valid comparisons are only possible between fixed length sFBM simulations. The
  power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD after time lags 40 \% the length of the trajectory
  with corresponding 95 \% intervals.
  %BJC3: Not sure if 40 % above is too long. I could do 20

  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We 
  incorporated uncertainty into transition probabilities by drawing samples from a 
  two dimensional Dirichlet distribution (also called a beta distribution) with concentration parameters defined by 
  the count matrix.~\cite{bacallado_bayesian_2009} We drew hops and dwells based on
  the current state of the system. We used a single Hurst parameter to describe
  correlation between hops, independent of the solute's mode. Ideally, each mode
  would have its own Hurst parameter, but we did not observe enough long sequences
  of uninterrupted time spent in each mode with which to generate robust
  autocorrelation functions.

  %We also projected MSDs out to 1 second for each solute. % BJC3:??
  %BJC3: not sure how to cite fbm
  We used the python package \texttt{fbm} to generate exact simulations of FBM and our
  own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  ~\cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories, however, the algorithm
  we used sufficiently approximates draws from the marginal distribution and reasonably 
  approximates the correlation structure. We added an empirical correction to enhance
  the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
  of the Supporting Information).

%  When simulating 5 $\mu s$ FLM trajectories, we limited the maximum hop length to
%  be no larger than the largest hop observed in our MD simulations. L\'evy stable 
%  distributions often have heavy tails and an undefined variance which can give 
%  rise to arbitrarily long particle displacements. We do not observe hops longer 
%  than x nm in our simulations which emphasizes that these distributions are only 
%  an approximation. We avoid enormous and unrealistic hops problem by truncating 
%  the tails of the distribution.

%  An important feature 
%  of L\'evy distributions is their heavy tails. Generally, a lower L\'evy index is 
%  characteristic of heavier tails, meaning higher probabilities of extremely large jumps.
%  In practical applications these extremely large hop lengths are unrealistic, especially
%  when comparing to MD.

  When simulating MD-length FLM trajectories, we limited the maximum hop length based on where
  the empirical hop distribution began to significantly under-sample the theoretical
  maximum likelihood estimate (MLE) L\'evy stable distribution (see 
  Section~\ref{S-section:truncation} of the Supporting Information).

  % TODO?: This vvvv
  For our 1 second simulations, we limited the maximum hop length to that seen by
  the same solute undergoing Brownian motion in an unconfined aqueous environment. 
  We have no reason to believe there is any kind of facilitated diffusion, so 
  excursions characteristic of Brownian motion represent a reasonable upper limit
  on hop lengths. To determine these limits we placed 24 solutes in a cubic box of 
  water, 4 nm on each side. We allowed the solutes to diffuse for 100 ns, more than
  ensuring the mean squared displacement entered a linear regime. We recorded the largest
  observed hop length over a 0.5 ns time lag.

  \subsection{Markov State-Dependent Dynamics}\label{method:MSMs}

  A Markov state model (MSM) decomposes a time series into a set of discrete states
  with transitions between states defined by a transition probability matrix, $T$,
  which describes the conditional probability of jumping to a specific state given
  the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
  dimensional reduction.

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. Therefore, there is no need to subject
  our trajectories to any reduction in dimensionality. 
  %However, we do adopt the
  %validation techniques used in the packages mentioned above. 
  The states we've 
  chosen include all combinations of trapping mechanisms in the pore and out of
  the pore (see Table~\ref{table:states}). We use the same radial cut-off (0.75 nm)
  as in the anomalous diffusion model to differentiate the pore and tail region. 
  These state choices assume that there are no significant kinetic effects resulting
  from solute conformational changes or pore size fluctuations, an assumption that
  may be relaxed in future work.

  \begin{table}[!htb]
	  \centering
      %MRS3: tweaked formatting, change back if you want!
      %BJC3: I don't like the centering much
	  \begin{tabular}{|l|l|}
	  \hline
	  1. In tails, not trapped                     & 5. In pores, not trapped                     \\
	  2. In tails and hydrogen bonding             & 6. In pores and hydrogen bonding             \\
	  3. In tails and associated with sodium       & 7. In pores and associated with sodium       \\
	  4. In tails, hydrogen bonding and associated & 8. In pores, hydrogen bonding and associated \\
	  \hline
	  \end{tabular}
	  \caption{We defined 8 discrete states based on all combinations of previously observed solute
	  trapping mechanisms}\label{table:states}  
	  %BJC3: the caption will depend on the journal. I don't
	  % like that J Phys Chem B forces the captions as titles, but if we choose them I think it would
	  % be cleaner to make the caption more title-like.
 \end{table}

  % BJC: does it make sense to use Dirichlet Process as a conjugate prior for
  % getting error on transition matrix?
  % BJC1: aha yes! \cite{bacallado_bayesian_2009}

  We constructed the state transition probability matrix, $T$, based on observed solute trajectories.
  Using methods described in our previous work, we determined each solute's radial location 
  and which, if any, trapping mechanisms affected it at each time step, then assigned the 
  observation to a specific state according to the definitions in Table~\ref{table:states}.~\cite{coscia_chemically_2019}
  Analogous to the mode transition matrix in Section~\ref{method:model_sFBM}, and based on
  the current and previous state observation, we incremented the appropriate entry of an
  $n~\times~n$ count matrix by 1, where $n$ is the number of states.

  We verified the Markovianity of our process by analyzing the transition matrix. An 
  important condition of a Markov process is the satisfaction of detailed balance:
  \begin{equation}
  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
  \end{equation}
  where $P$ is the equilibrium distribution of states. In other words, the number of
  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
  test is to verify that $T$ holds up to a coarser time scale.~\cite{swope_describing_2004}
  We verified these properties in Section~\ref{S-section:markov_validation} of the 
  Supporting Information.

  % BJC3: This explanation is in previous section
  %For example, if 
  %we observed state 1 followed by a transition to state 3, we increment the $(1, 3)$ entry
  %of the count matrix by 1. We generate the transition probability matrix from the count matrix by 
  %normalizing the entries in each row so that they summed to unity.

  Adding to the standard MSM framework, we attempted to incorporate the dynamics within 
  each state as well as the dynamics of state transitions. While MSMs are often used to 
  gauge equilibrium populations of various states, adding dynamics will allow us to  % BJC3 a reference would be good.
  more accurately simulate solute trajectories. Hence we distinguish our model from 
  MSMs by referring them as Markov State-Dependent Dynamical Models (MSDDMs).

  We recorded the $z$-direction displacement at each time step in order to construct 
  individual emission distributions for each state and transition between states. 
  This results in 64 distinct emission distributions with some far more populated than
  others. We modeled all of the emission distributions as symmetric L\'evy stable 
  distributions in order to maintain flexibility in parameterizing the distributions.

  We observed negatively correlated hops within each state and among transitions between
  states. We can use the Hurst parameter to describe this negative time series correlation
  however, there is not sufficient data to accurately measure a Hurst parameter for 
  each type of transition. We avoided this problem by treating transitions as correlated
  emissions from a single L\'evy stable distribution. This reduces the number of emission
  distributions from 64 to 9 (1 for each state and 1 for transitions between states).

  We simulated realizations of the MSDDM using the probability transition matrix and 
  emission distributions. For each trajectory simulated, we chose an initial state
  randomly from a uniform distribution. We generated a full state sequence by randomly
  drawing subsequent states weighted by the rows of the probability transition matrix
  corresponding to the particle's current state. Again we incorporated uncertainty into
  the rows of the transition matrix by resampling them from a Dirichlet distribution. 
  For each same-state subsequence of the full state sequence, we simulated an FLM process
  using the Hurst parameter of that state and the parameters of the corresponding emission
  distribution. Independently, we simulated the transition between each same-state 
  sequence with an FLM process based on the Hurst parameter of transition sequences and 
  the parameters of the single transition emission distribution. We used the same FLM 
  simulation procedure described in Section~\ref{method:model_sFBM}.

%  corresponding emissions from the rows of the probability transition matrix and the 
%  appropriate emission distribution respectively. We added correlation between transitions
%  as well as to sequences of emissions while dwelling in specific states using the FLM
%  simulation procedure described in Section~\ref{method:model_sFBM}.

  % BJC: need to add some validation of Markovian behavior and time step choice.

  \section{Results and Discussion}

% BJC3: Don't think this section is needed
%  \subsection{Molecular Dynamics Simulations}\label{section:MD_simulations}
%  
%  The MSDs for of the solutes calculated from 5 $\mu s$ MD simulation trajectories
%  are shown in Figure TBD.
%  \begin{itemize}
%    %MRS: probably option 1.
%    \item 2 options for a figure:
%    \item 1) 2 panels: 1st panel: bar chart with final MSD value + error bars. 2nd panel: a selected MSD curve
%    \item 2) 1 panel. All MSD curves. Overlapping errors might look bad
%  \end{itemize}
%  
%  %MRS: I'm not sure where the below is different from what was found in the previous study (i.e MSD's).
%  % BJC1: move to supporting if included
%%  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
%%  previous work.
%%  \begin{itemize} 
%%    \item The extent to which each trapping mechanism influences each solute is
%%  	depicted graphically in Figure TBD.
%%    \item Same types of figures from transport paper:
%%    \item Fraction participating in hydrogen bonds, fraction associated, fraction
%%    in the tails.
%%    \item Lifetimes of hbonds and sodium associations?
%%  \end{itemize}
%
%  Methanol and acetic acid are not fully equilibrated, therefore we did not use them
%  to test our models.

  \subsection{Anomalous Diffusion Modeling}\label{section:sFBM}

  We believe that solutes in this system can be well-modeled by subordinated fractional
  Brownian motion. The solutes clearly perform jumps after periods of relative immobility
  (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}.

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_trajectories.pdf}
  \caption{}\label{fig:solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{(a) Urea exhibit hops between periods of entrapment, characteristic of a CTRW. 
  (b) The distribution of hop lengths fits well to a Gaussian as well as a more general L\'evy 
  stable distribution. The L\'evy stable distribution does a better job of capturing the 
  heavier tails and increased density near 0. (c) The distribution of dwell times is fit
  well by a power law but it may over-estimate the probability density at long dwell times.
  A power law truncated with an exponential cut-off may better describe the probability of
  long dwell times in our simulations. (d) The hops are negatively correlated to their previous
  hop. In combination (a) -- (d) support modeling solutes as subordinated fractional Brownian
  motion. The behavior shown by Urea in this figure is common to all solutes in this study.}\label{fig:anticorrelated_hops}
  \end{figure}

  We modeled the distributions of hop lengths in two ways. First, we assumed the 
  distribution to be Gaussian since it is possible to exactly simulate realizations of
  fractional Brownian motion. Second, we fit the distributions to L\'evy stable 
  distributions since it is more general than the Gaussian distribution. We plotted
  the MLE fits of both on top of Urea's hop length distribution in 
  Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a better
  job capturing the heavy tails and high density near 0 of the hop length distribution.
  However, since there are no known exact simulation techniques for generating 
  realizations of fractional L\'evy motion, we must explore whether this more general
  fit is worthwhile.

  We also modeled the distribution of dwell times in two ways. First, we assumed pure
  power law behavior since it is consistent with most theoretical descriptions of CTRWs.
  The data fits well to this model at short dwell times but
  the density of long dwell times is over-estimated. In our second approach, we truncate
  the power law distribution with an exponential cut-off, lowering the probability of
  long dwell times. We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where the
  density of the truncated power law drops below that of the pure power law and tends towards
  0 near a dwell time of 250 ns.

  The model parameters are tabulated in Tables~\ref{table:sfbm_params} 
  and~\ref{table:sfbm_params_2mode} and tell their own story about each solute's behavior. Using the 
  techniques from Section~\ref{method:model_sFBM}, we extracted parameter values for each
  solute in order to create 1 and 2 mode models, displayed in Tables~\ref{table:sfbm_params} 
  and~\ref{table:sfbm_params_2mode} respectively. Higher values of $\sigma$ and lower
  values of $\alpha_h$ indicate larger average hop length magnitudes by increasing the
  hop length distribution's width and tail density respectively. Higher values of $\alpha_d$
  indicate a lower probability of long dwell times. Higher values of $\lambda$ truncate
  the power law distribution earlier preventing extremely long dwell times. Values of $H$
  closer to the Brownian limit of 0.5, indicate a lower degree of negative correlation 
  between hops. All of which contribute to an overall increase in the MSD.

  The parameters of the 1 mode model are similar between urea and ethylene glycol which 
  is not surprising considering their similar MD MSDs. Dwell times by 
  ethylene glycol are shorter as shown by its larger $\alpha_d$ and $\lambda$ values. Both
  solutes make similarly sized hops with hop distributions that are relatively close 
  to Gaussian (i.e. $\alpha_h$ near 2) when fit to a L\'evy stable distribution. Finally,
  both solutes exhibit a similar degree of correlation between hops with ethylene glycol
  exhibiting motion closer to Brownian.

  The parameters of the 2 mode model are again similar between urea and ethylene glycol, 
  but the difference between parameters of each mode offer more detailed mechanistic
  insight than the 1 mode model. It is clear that solutes are significantly slowed while
  they are in the tail region where long dwell times are more probable and hops are 
  smaller. Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
  heavy tailed relative to ethylene glycol which has an $\alpha_d$ more consistent 
  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
  the tails, it still has an appreciable probability of making large hops. This could 
  be a consequence of urea's small profile. Ethylene glycol is a linear chain that can
  easily become entangled among the alkane tails while urea is planar with its four
  heavy atoms bonded to a single central atom.

  % BJC3: is it worth trying to combine these tables?
  % BJC: note to self -- modes are flipped in simulation output because 
  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol \\
  \hline
  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            \\\cline{2-4}
  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    \\\hline
  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            \\\cline{2-4}
  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      \\\hline
  Correlation   & $\gamma(H)$               & 0.37         & 0.40            \\
  \hline 
  \end{tabular}
  \caption{To create a 1 mode model for each solute, we parameterized a pure power
  law ($P(\alpha_d)$) and a truncated power law $P_T(\alpha_d, \lambda)$ distribution 
  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
  law tails and higher values of $\lambda$ truncate the distribution at lower
  dwell times. We paramterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
  function ($\gamma(H)$) to describe the degree of correlation between hops. 
  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
  \end{table}

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  \multicolumn{5}{|c|}{2 Mode Model} \\\hline
                & Parameters                               & Mode & Urea         & Ethylene Glycol \\
  \hline
                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           \\\cline{3-5}
  Dwell         &                                          & 2    & 0.38         &  0.48           \\\cline{2-5}
  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   \\\cline{3-5}
                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   \\\hline
                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           \\\cline{3-5}
  Hop           &                                          & 2    & 0.24         &  0.23           \\\cline{2-5}
  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     \\\cline{3-5}
                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     \\\hline
  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           \\\cline{3-5}
  \hline 
  \end{tabular}
  \caption{To create a 2 mode model, we generated a set of parameters based on solute
  behavior as function of distance from the pore center. Mode 1 corresponds to solute
  behavior within 0.75 nm of the pore center and mode 2 corresponds to behavior greater
  than or equal to 0.75 nm from the pore center. Note that we used the same Hurst parameter
  for both modes due to a low number of sufficiently long sequences of hops in each mode. 
  See Table~\ref{table:sfbm_params} for descriptions of the parameters.}\label{table:sfbm_params_2mode}
  \end{table}

  Our models reasonably predict the MD simulated MSDs. Using the parameters in 
  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} as inputs, we compared
  the MSD of simulated anomalous diffusion trajectories to MD simulated MSDs. The MSD
  curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs
  for comparison in Figures~\ref{fig:anomalous_msds_1mode} and 
  Figure~\ref{fig:anomalous_msds_2mode} respectively.

  %BJC3: wondering if I should cut these plots off at 20 % of total equilibrated simulation time instead of 40.
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE.pdf}
  \caption{Urea}\label{fig:1mode_msd_comparison_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:1mode_msd_comparison_GCL}
  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{1mode_msd_comparison_MET.pdf}
%  \caption{Methanol}\label{fig:1mode_msd_comparison_MET}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH.pdf}
%  \caption{Acetic Acid}\label{fig:1mode_msd_comparison_ACH}
%  \end{subfigure}
  \caption{MSDs generated from realizations of our 1 mode anomalous diffusion models
  agree well with MD-generated data. When we do not apply an exponential cut-off to the
  dwell time distribution (sFBM and SFLM), MSDs are underpredicted. Drawing hops from
  a truncated L\'evy stable distribution results in higher MSDs than draws from Gaussians.}\label{fig:anomalous_msds_1mode}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE.pdf}
  \caption{Urea}\label{fig:2mode_msd_comparison_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:2mode_msd_comparison_GCL}
  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{2mode_msd_comparison_MET.pdf}
%  \caption{Methanol}\label{fig:2mode_msd_comparison_MET}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH.pdf}
%  \caption{Acetic Acid}\label{fig:2mode_msd_comparison_ACH}
%  \end{subfigure}
  \caption{MSDs generated from realization of our 2-mode anomalous diffusion model
  also match well to MD-generated data. The MSD of Urea appears to be underpredicted
  by all model combinations. The MSD of ethylene glycol is predicted well when 
  we draw dwell times from a power law distribution with an exponential cut-off.}\label{fig:anomalous_msds_2mode}
  \end{figure}

  Truncating the power laws with an exponential cut-off has the largest effect on the on 
  the match between MD MSD and simulated anomalous diffusion trajectories. Without 
  truncation, the MD MSDs are underestimated. This is because dwell times on the order 
  of the MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories, reducing the MSD. The longest observed dwell time among the
  solutes was 1.3 $\mu$s by ethylene glycol.

  %BJC3: simulated anomalous diffusion --> SAD ? HMM kind of a downer
  Simulated anomalous diffusion trajectories which draw from a L\'evy stable distribution
  generally predict higher MSDs. The heavy tails of the distribution incorporate large
  jumps more frequently into the trajectories. The only exception is that of ethylene
  glycol in the 2 mode model where the L\'evy index for both modes is near 2, indicating
  a near Gaussian distribution, but the MLE of the $\sigma$ values of the L\'evy stable
  distribution are much smaller than the Gaussian MLE $\sigma$ values.
  %BJC3: I need to investigate this. How could sigma be so far underestimated if basically Gaussian

  % BJC3: I'd like to present the parameter values because they give clues
  % towards mechanisms
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|c|c|c|c|c|}
%  \hline
%  \multirow{4}{*}{Model} & \multicolumn{4}{c|}{Urea} \\\cline{2-5}
%  & \multicolumn{4}{c|}{Single Mode (H = 0.37)} \\\cline{2-5}
%  & \multicolumn{2}{c|}{Dwells} & \multicolumn{2}{c|}{hops} \\\cline{2-5}
%  & $\alpha$ & $\lambda$ & $\sigma$ & $\alpha$ \\\hline
%  sFBM   & 0.57 & --     & 0.33 & --   \\
%  sFBMcut& 0.40 & 0.0024 & 0.33 & --   \\
%  sFLM   & 0.57 & --     & 0.21 & 1.84 \\
%  sFLMcut& 0.40 & 0.0024 & 0.21 & 1.84 \\
%  \hline
%  \end{tabular}
%  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
%  trajectories and then computed the average ensemble-averaged MSD of 10000 
%  simulated trajectories.}\label{table:sfbm_params}
%  \end{table}

%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
%  \hline
%  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol & Methanol & Acetic Acid \\
%  \hline
%  Dwell         & $P(\alpha_d)$             & 0.57         & & & \\
%  Distributions & $P_T(\alpha_d, \lambda)$  & (0.4, 0.0024)& & & \\
%  \hline
%  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & & & \\
%  Distributions & $L(\sigma, \alpha_h)$     & (0.21, 1.84) & & & \\
%  \hline
%  Correlation   & $\gamma(H)$               & 0.37         & & & \\
%  \hline 
%  \end{tabular}
%  \caption{To create a 1 mode model for each solute, we parameterized a pure power
%  law ($P(\alpha_d)$) and a truncated power law $P_T(\alpha_d, \lambda)$ distribution 
%  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
%  law tails and higher values of $\lambda$ truncate the distribution at lower
%  dwell times. We paramterized Gaussian ($\mathcal{N}$) and L\'evy stable 
%  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
%  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
%  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
%  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
%  function ($\gamma(H)$) to describe the degree of correlation between hops. 
%  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
%  \end{table}
%  
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
%  \hline
%  2 Mode Model  & Parameters                               & Mode & Urea         & Ethylene Glycol & Methanol & Acetic Acid \\
%  \hline
%                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.57         & & & \\\cline{3-7}
%  Dwell         &                                          & 2    & 0.57         & & & \\\cline{2-7}
%  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    &(0.4, 0.0024) & & & \\\cline{3-7}
%                &                                          & 2    &(0.4, 0.0024) & & & \\\hline
%                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.33         & & & \\\cline{3-7}
%  Hop           &                                          & 2    & (0.21, 1.84) & & & \\\cline{2-7}
%  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.33         & & & \\\cline{3-7}
%                &                                          & 2    & (0.21, 1.84) & & & \\\hline
%  \multirow{2}{*}{Correlation}&\multirow{2}{*}{$\gamma(H)$}& 1    & 0.37         & & & \\\cline{3-7}
%                &                                          & 2    & 0.37         & & & \\\cline{3-7}
%  \hline 
%  \end{tabular}
%  \caption{To create a 2 mode model, we generated a set of parameters based on solute
%  behavior as function of distance from the pore center. Mode 1 corresponds to solute
%  behavior within 0.75 nm of the pore center and mode 2 corresponds to behavior greater
%  than or equal to 0.75 nm from the pore center. See Table~\ref{table:sfbm_params}
%  for descriptions of the parameters.}\label{table:sfbm_params_2mode}
%  \end{table}

  %BJC3: Is it a bad idea to acknowledge that there is no experimental data? I can 
  % spin this paragraph in a different way.
  Choosing which model to use for long timescale projections is not entirely obvious
  without experimental data to compare with. For our comparisons to MD, using a 
  truncated power law distribution is an obvious choice. However, given that extremely
  long dwells are a rare event, it is possible that studying a much larger set of 
  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
  distributions, the generality of L\'evy stable distributions is powerful, but the
  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
  accuracy and computational tractability. Treating the dynamics as fractional 
  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is well below 2.

%  \noindent We can use the model to project our simulations out to very long timescales.
%  \begin{itemize}
%    \item We can not definitively say which combination of distributions are best to use.
%    \item Although the longest observed dwell times and hop lengths are less than
%    the length of the simulated trajectories and box lengths respectively, it is still possible
%    that that extremely long dwell times and hops are observed experimentally in rare but
%    significant cases.
%    \item We present long timescale projections using combinations of each distribution in the
%    table below
%  \end{itemize}

  % BJC2: table of long timescale projections using combinations of dwell and hop distributions. 
  %% TABLE %%

  \subsection{Markov State-Dependent Dynamics}\label{section:msm_results}

  To create an MSDDM for each solute, we generated emission distributions based 
  on transitions from each state and transitions between states. There are not
  enough consecutive observations of each type of transition with which to study
  their individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.

  We observe correlated emissions drawn from L\'evy stable distributions.
  The deviation of the emission distributions from Gaussian behavior is far more pronounced
  than that seen in the hop length distributions of the previous section, therefore we 
  did not consider the Gaussian case (see Figure~\ref{fig:gaussian_levy_comparison}).
  The correlation structure between hops resembles that of FLM (Figure~\ref{fig:msddm_acf}).
  The parameters of the L\'evy stable distributions along with their Hurst parameters 
  are tabulated in Table~\ref{table:msddm_params}.

  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) Emission distributions are non-Gaussian and heavy-tailed. Shown here is the
  emission distribution for transitions between states. The maximum likelihood
  Gaussian fit severely underestimates the empirical density of hops near and far from zero 
  while overestimating the density of hops at intermediate values. (b) Jumps drawn from
  the transition distribution are negatively correlated to each other. The normalized version 
  of Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
  an appropriate way to model jumps.} \label{fig:msddm_emissions}
  \end{figure}

%  %BJC3: TODO automate this table
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
%  \hline
%  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
%  State & H     & $\alpha$ & $\sigma$ & H    & $\alpha$ & $\sigma$ & H & $\alpha$ & $\sigma$ & H & $\alpha$ & $\sigma$ \\\hline
%  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045    &   &          &           &  &          &           \\
%  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037    &   &          &           &  &          &           \\
%  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030    &   &          &           &  &          &           \\
%  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028    &   &          &           &  &          &           \\
%  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062    &   &          &           &  &          &           \\
%  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040    &   &          &           &  &          &           \\
%  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040    &   &          &           &  &          &           \\
%  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030    &   &          &           &  &          &           \\
%  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045    &   &          &           &  &          &           \\\hline
%  \end{tabular}
%  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
%  trajectories and then computed the average ensemble-averaged MSD of 10000 
%  simulated trajectories.}\label{table:msddm_params}
%  \end{table}
%  
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
%  \hline
%  & \multicolumn{4}{c|}{Urea}                      & \multicolumn{4}{c|}{Ethylene Glycol} \\\hline
%  State & H     & $\alpha_h$ & $\sigma$ & $T_{ii}$ & H    & $\alpha_h$ & $\sigma$ & $T_{ii}$  \\\hline
%  1     & 0.10  & 1.79       & 0.034    &  0.60    & 0.09 & 1.68       & 0.045    & 0.41 \\
%  2     & 0.06  & 1.80       & 0.033    &  0.38    & 0.09 & 1.75       & 0.037    & 0.58 \\
%  3     & 0.11  & 1.88       & 0.030    &  0.73    & 0.11 & 1.86       & 0.030    & 0.21 \\
%  4     & 0.10  & 1.95       & 0.027    &  0.57    & 0.04 & 1.91       & 0.028    & 0.34 \\
%  5     & 0.19  & 1.34       & 0.048    &  0.62    & 0.15 & 1.40       & 0.062    & 0.47 \\
%  6     & 0.15  & 1.45       & 0.040    &  0.38    & 0.11 & 1.52       & 0.040    & 0.62 \\
%  7     & 0.15  & 1.61       & 0.032    &  0.61    & 0.05 & 1.60       & 0.040    & 0.15 \\
%  8     & 0.11  & 1.71       & 0.028    &  0.41    & 0.05 & 1.74       & 0.030    & 0.29 \\
%  T     & 0.34  & 1.42       & 0.036    &   --     & 0.37 & 1.44       & 0.045    &  --  \\\hline
%  \end{tabular}
%  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
%  trajectories and then computed the average ensemble-averaged MSD of 10000 
%  simulated trajectories. The states are defined in Table~\ref{table:states}
%  except state T which refers to the transition emissions.}\label{table:msddm_params}
%  \end{table}

  \begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Urea}                      & \multicolumn{3}{c|}{Ethylene Glycol} \\\hline
  State & H     & $\alpha_h$ & $\sigma$  & H    & $\alpha_h$ & $\sigma$ \\\hline
  1     & 0.10  & 1.79       & 0.034     & 0.09 & 1.68       & 0.045    \\
  2     & 0.06  & 1.80       & 0.033     & 0.09 & 1.75       & 0.037    \\
  3     & 0.11  & 1.88       & 0.030     & 0.11 & 1.86       & 0.030    \\
  4     & 0.10  & 1.95       & 0.027     & 0.04 & 1.91       & 0.028    \\
  5     & 0.19  & 1.34       & 0.048     & 0.15 & 1.40       & 0.062    \\
  6     & 0.15  & 1.45       & 0.040     & 0.11 & 1.52       & 0.040    \\
  7     & 0.15  & 1.61       & 0.032     & 0.05 & 1.60       & 0.040    \\
  8     & 0.11  & 1.71       & 0.028     & 0.05 & 1.74       & 0.030    \\
  T     & 0.34  & 1.42       & 0.036     & 0.37 & 1.44       & 0.045    \\\hline
  \end{tabular}
  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
  trajectories and then computed the average ensemble-averaged MSD of 10000 
  simulated trajectories. The states are defined in Table~\ref{table:states}
  except state T which refers to the transition emissions.}\label{table:msddm_params}
  \end{table}

  Most of a solute's MSD is a consequence of transitions between the 8 states
  in Table~\ref{table:states}. Motion while trapped in a state is highly 
  anti-correlated as indicated by their consistently low Hurst parameters.
  The Hurst parameters for transitional emissions are 2-9 times higher than
  emissions from trapped states. The value of $\alpha_h$ for transition 
  emissions is also relatively low giving higher probabilities to larger hops.

  As solutes are influenced by more trapping effects, the width of the hop length
  distribution, $\sigma$, decreases while its L\'evy index increases. Treating the
  tail and pore regions independently, $\sigma$ is largest and $\alpha_h$ is lowest
  when solutes are not hydrogen bonding or associating with sodium (states 1 and 5).
  Solutes are free to move and take occasionally large hops. The smallest $\sigma$
  and highest $\alpha_h$ values are measured when solutes are hydrogen bonding and 
  associating with sodium at the same time (states 4 and 8). Motion is restricted 
  by multiple tethers which maintains a relatively narrow distribution of hop lengths.

  The trapping mechanisms affect each solute to varying degrees. The probabilities
  of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
  Urea and ethylene glycol spend 56 \% and 44 \% of their time in the tails
  respectively. Urea's compact and flat structure allows it to more easily 
  partition into the tails while ethylene glycol prefers the pore region due to 
  its two hydrophilic hydroxyl groups.

  Urea spends the largest fraction of its time associated with sodium ions.
  It does so 31 \% of the total time while in the tails (state 3) and 21 \%
  of the total time while in the pores (state 7). The electron-dense and 
  unshielded oxygen atom of urea's carbonyl group are prone to associate 
  with positively charged sodium ions. The nitrogen atoms of urea are only
  weak hydrogen bond donors.

  Ethylene glycol spends the largest fraction of its time hydrogen bonding.
  It does so 24 \% of the total time while in the tails (state 2) and 32 \% 
  of the total time while in the pores (state 6). The two hydroxyl groups 
  of ethylene glycol readily donate their hydrogen atoms to the carboxylate
  head groups and the ether linkages between the head groups and monomer tails.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{state_probabilities.pdf}
  \caption{The probability of finding urea or ethylene glycol in a given state.}\label{fig:state_probabilities}
  \end{figure}

  %BJC3: show how much of the MSD comes from each? Not sure this will work because of transition matrix dependence
  %BJC3: can just say

  % BJC2: This figure will show predicted MSDs versus MD MSDs
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_msddm.pdf}
  \caption{}\label{fig:URE_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_msddm.pdf}
  \caption{}\label{fig:GCL_msddm}
  \end{subfigure}
  % BJC3: these need more data
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{URE_msddm.pdf}
%  \caption{}\label{fig:MET_msddm}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{GCL_msddm.pdf}
%  \caption{}\label{fig:ACH_msddm}
%  \end{subfigure}
  \caption{MSDs predicted by the MSDDM significantly over-predict those
  from generated from MD simulations.}\label{fig:msddm_performance}
  \end{figure}

  %BJC3: would take ~ 20 hours to simulation 10000 trajectories.
  The MSDDM over-estimates solute MSDs (see Figure~\ref{fig:msddm_performance}). 
  We simulated 1000 trajectories as described in Section~\ref{method:MSMs} then
  %BJC3: 2.2 and 3.3 x higher than MD to be exact
  calculated their MSDs. The MSD of urea and ethylene glycol are about 2 and 3 times
  higher than MD simulations respectively.

  The MSDDM overestimates solute MSDs because we simulated each state
  sequence independently. Although correlation exists within each
  sequence, there is no memory of the previous state or state transition 
  that can be built into the first emission of the most recent state. 
  This implies that the first value in a state sequence is a random
  draw from the underlying emission distribution. Frequent transitions
  between states lead to an abundance of short dwell times. It is 
  difficult to accurately correlate short sequences so we are 
  almost simulating uncorrelated draws from the emission distribution.
  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying 
  the transition matrix and simulating a simple 2-state model with parameters
  similar to those in Table~\ref{table:msddm_params} (see Table~\ref{S-table:msddm_params}
  of the Supporting Information). We modified the probability
  transition matrix, $T$, in order to control the probability of 
  self-transitions (the diagonal elements of $T$). Larger self-transition probabilities lead to longer dwell 
  times in each state. We set the off-diagonal elements of $T$ to be equal values that make the
  rows of $T$ sum to unity when combined with the self-transition probabilities. 
  As we increase the self-transition probability, $T_{ii}$, the simulated MSD 
  decreases. Longer dwell times in each state allow us to more accurately
  simulate the negative correlation that we observe in MD.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{T_sensitivity.pdf}
  \caption{As we increase the self-transition probabilities ($T_{ii}$) of an MSDDM,
  the simulated MSD of the process decreases because the negative correlation structure
  of individual state sequences is simulated more accurately.}\label{fig:T_sensitivity}
  \end{figure}

  The MSDDM offers mechanistic insight but cannot be used for reliable predictions
  of solute MSDs. It may be suitable for processes with rarer transitions between 
  states. If we can further reduce the state-space of our models, the MSDDM
  may have better predictive success, but we lose mechanistic detail.

%  We projected the long timescale behavior using this model.

  \section{Conclusion}

  % MRS1: will want to make a statement about whether these approaches
  % are together good enough for predictive purposes, and if not,
  % explore what else should be done in the future.
  % BJC2: It seems like it would be hard to make say these can be used
  % for prediction without experimental confirmation of the trends that we observe.

  We have tested two different mathematical frameworks for describing solute
  motion in an H\textsubscript{II} phase LLC membrane. The parameters of each model offer mechanistic insight.
  Subordinated fractional Brownian and L\'evy motion have a nice theoretical 
  foundation in the anomalous diffusion literature. Our single mode model
  quantifies and allows comparison of the hopping and trapping behavior 
  between solutes. A two mode model that describes dynamics based on whether
  a solute is in or out of the pore region allows us to break down individual
  solute motion into the two distinct regimes. We showed that solute motion is
  clearly restricted while in the tail region. Our Markov state-dependent dynamical
  model uses explicitly defined trapping mechanisms and gives a nice description 
  of transitions between these observed states, the equilibrium distribution of 
  solutes among states as well as the type of stochastic behavior shown in each 
  state. However, it doesn't accurately portray correlated time series behavior
  leading to overpredicted MSDs.

  We believe that our models have moderate predictive power. The anomalous
  diffusion model has superior performance to the MSDDM. Both 1 and 2 mode 
  sFBM and sFLM with truncated power law distributions predict MSDs close 
  to those simulated with MD while the MSDDM significantly over-predicts MSDs.
  One might have more success using the MSDDM with a system that exhibits
  infrequent transitions between states.

  Our mathematical models help us think about how to design LLC monomers for 
  solute-specific separations by forcing us to think in terms of controlling 
  solute trapping. The anomalous diffusion model is quite flexible because it
  does not require knowledge of specific trapping mechanisms. Screening a set
  of solutes and applying the anomalous diffusion model can help uncover
  trapping mechanisms by forcing the scientist to identify features common 
  to solutes with long or short hop lengths and dwell times. The MSDDM is a 
  powerful way to characterize explicit trapping mechanisms. Although its
  predictive power is inferior to the anomalous diffusion model, it clearly
  partitions a trajectory into discrete mechanisms and quantifies their
  relative dominance in the real system. For example, it is clear that 
  sodium ion association is primarily responsible for trapping Urea while 
  hydrogen bonding dominates ethylene glycol. If one redesigns an LLC monomer
  to eliminate one source of trapping, then high selectivities are possible.

%  Properly parameterizing
%  and simulating the correlation structure of the time series is very important. 
%  Based on physical intuition, we assumed the correlation to be a consequence of 
%  a fractional process however, autoregressive techniques may offer a more flexible
%  approach.
% Both models describe the trapping mechanism in
%  different ways. The anomalous diffusion model does not consider mechanisms but
%  insight into the length of entrapment
%  
%  The anomalous diffusion gives clues to the type 
%  of functionality that leads to long dwell times. It is readily apparent that solute 
%  
%  One must consider how to control them and 
%  a solute's preference towards the pore or tail region. 
%  They can dissect solute movement down to their 
%  individual positional fluctuations and give information about the influence 
%  of the surrounding chemical environment. 
%
%  
%  Combined with qualitative studies of solute transport to aid in model construction,
%  our stochastic modeling framework can be used to quantitatively dissect the dynamic
%  behavior of solutes in LLC membranes. Our work demonstrates that when designing a membrane for a 
%  specific separation, one must consider the types of trapping mechanisms that 
%  may play a role in transport, how solutes partition in the membrane,

  \section*{Supporting Information}

  Detailed explanations and expansions upon the results and procedures mentioned in
  the main text are described in the Supporting Information. This information is
  available free of charge via the Internet at http://pubs.acs.org.

  \section*{Acknowledgements}

  %MRS3: add specific info for PRF and GAANN
  %BJC3: I don't know the PRF info. I wrote GAANN as I did on the last paper which is what Rob Davis told me to do
  This work was supported in part by the ACS Petroleum Research Fund grant XXXXXX 
  and the Graduate Assistance in Areas of National Need (GAANN)
  fellowship which is funded by the U.S. Department of Education.
  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  \clearpage

  \bibliographystyle{ieeetr}
  \bibliography{stochastic_transport}

  \newpage

  \section*{TOC Graphic}

\end{document}

### 2019-10-04 Ben_Manuscripts/catalysis/Supporting_Information.tex
Supporting work towards Greg's catalysis paper

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thetable}{S\arabic{table}}

\title{Supporting Information: Modeling Monomer Interactions with Molecular Dynamics}

\begin{document}

  \graphicspath{{./figures/}}
  \maketitle
  \bibliographystyle{ieeetr}

  We used an atomistic molecular model and molecular dynamics simulations 
  in order to quantify the number of acid-base reactions that would occur in
  a real system as a pure consequence of proximity. We ran all MD simulations
  and energy minimizations using GROMACS 2018.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
  We built and equilibrated initial configurations and performed post-simulation trajectory 
  analysis using python scripts which are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  Table~\ref{table:python_scripts} provides more detail about specific scripts
  used for each task.

  \begin{table}[htb!]
  \centering
  \newcolumntype{A}{m{2in}}
  \newcolumntype{C}{m{4in}}
  \begin{tabular}{|A|C|}
  \hline
  \multicolumn{1}{|c|}{\textbf{Script}}  & \multicolumn{1}{c|}{\textbf{Purpose}}                  \\ \hline

  \texttt{/setup/build.py}               & Build initial configuration                            \\ \hline
  \texttt{/setup/equil.py}               & Energy minimize and equilibrate initial configurations \\ \hline
  \texttt{/analysis/hbonds.py}           & Identify hydrogen bond interactions based on angle 
                                           and distance cut-off criteria.                         \\ \hline
  \texttt{/analysis/hbond\_reactions.py} & Track cumulative number of reacted acid-base pairs 
                                           using hydrogen bonds as a reaction surrogate           \\ \hline

  \end{tabular}

  \caption{The first column provides the names of the python scripts available in
  the \texttt{LLC\_Membranes} GitHub repository that were used for system setup and
  post-simulation trajectory analysis. Paths preceding script names are relative to the
  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second column provides a brief 
  description of the purpose of each script.}~\label{table:python_scripts}

  \end{table}

  We constructed four independent simulation unit cells on which to collect data.  
  The monoclinic unit cells consist of four pores, each made of 5 columns of 20
  monomers stacked on top of each other 3.7 \AA~apart in a parallel displaced 
  configuration (see Figure~\ref{fig:system_setup}). We randomly distributed the
  acidic and basic monomers among the columns. The parallel displaced $\pi-\pi$ 
  stacking configuration is more stable than the sandwiched configuration
  where monomers stack directly on top of each other.~\cite{sinnokrot_estimates_2002}
  In previous work with a similar monomer, we also found that systems built in the
  parallel displaced configuration as described above provide the closest match 
  to experimental structural data.~\cite{coscia_understanding_2019}

  \begin{figure}
  \centering
  \begin{subfigure}{0.34\textwidth}
  \includegraphics[width=\textwidth]{column.pdf}
  \caption{}\label{fig:column}
  \end{subfigure}
  \begin{subfigure}{0.56\textwidth}
  \includegraphics[width=\textwidth]{unitcell.pdf}
  \caption{}\label{fig:unitcell}
  \end{subfigure}
  \caption{(a) We randomly chose a total of 20 acidic (red) and basic (blue) 
  monomers and stacked the aromatic head groups in a parallel displaced 
  configuration on top of each other to form columns. (b) We created 4 pores, 
  each consisting of 5 columns, and placed them in a monoclinic unit cell (represented
  by the blue box) which is the smallest unit cell that preserves hexagonal 
  symmetry when the system is extended periodically. The pore centers are
  highlighted by the colored monomer head groups.}\label{fig:system_setup}
  \end{figure}

  We equilibrated the unit cells using the same procedure as our previous
  work.~\cite{coscia_understanding_2019} All steps of the following
  procedure are implemented in \texttt{LLC\_Membranes/setup/equil.py} 
  (see Table~\ref{table:python_scripts}):
  % BJC: I can write this in paragraph form if that would be better.
  \begin{enumerate}
  	\item Build initial configuration
  	\item Energy minimize initial configuration with high (1e6 $\frac{kJ}{mol \cdot nm^2}$)
  	position restraints on head group heavy atoms. 
  	\item Run 50 ps NVT simulation with same position restraints.
  	\item Repeat steps 2 and 3, gradually reducing the force constant on head
  	group heavy atoms according to the sequence 3162, 56, 8, 3, 2, 1, 0 $\frac{kJ}{mol \cdot nm^2}$.
  	\item Run 5 ns unrestrained NPT simulation with semi-isotropic pressure 
  	coupling controlled by the Berendsen barostat and temperature controlled by the 
  	v-rescale thermostat.
  	\item Run long ($> 400~ns$) NPT simulations with semi-isotropic pressure
  	coupling controlled by the Parinello-Rahman barostat and temperature controlled by
  	the v-rescale thermostat.
  \end{enumerate}

  Because MD simulations typically do not involve reactions, we used hydrogen
  bonding as a surrogate for the acid-base reaction that would deactivate
  catalytic monomers. We considered a reaction to occur if a COOH group of monomer
  \textbf{1} donated its hydrogen to the NH\textsubscript{2} group of monomer
  \textbf{2}. A study of hydrogen bonding patterns among thousands of structures 
  in the Cambridge Structural Database suggests that this type of hydrogen
  bond does not exist~\cite{gilli_predicting_2009}. This is likely because proton
  transfer is immediate and nearly irreversible. % BJC: could put pKa calculation here

  We predicted the percentage of unreacted monomers present in bulk film by
  counting the number of unique acid-base ``reactions'' as a function of time in 
  our MD simulations. In our search for hydrogen bonds, we considered each new 
  hydrogen bonded pair to be ``reacted'' and excluded both monomers from the rest
  of the search. We ran our simulations until the percentage of reacted monomers 
  plateaued for at least 100 ns.

  %As explained in the main text, clustering of acidic and basic monomers may prevent
  %an appreciable fraction of them from reacting with each other. 
  The exact percentage of unreacted monomers predicted from our simulations is a 
  function of the geometric criteria that we chose to use for identifying hydrogen bonds.
  There is no consensus in the simulation literature as to the proper way of identifying
  a hydrogen bond.~\cite{prada-gracia_quest_2013} In our previous work, we 
  defined a hydrogen bond to exist if the distance, $d$, between the donor (D) and acceptor (A)
  atoms was less than 3.5~\AA~and the D--H$\cdots$A angle, $\theta$, was less than 30\degree
  (see Figure~\ref{fig:hbond_geometry}).~\cite{coscia_chemically_2019} However, most
  of the hydrogen bonds were of the type O--H$\cdots$O whereas we are interested in
  O--H$\cdots$N. Studies of structurally similar hydrogen bonds show a range of 
  behavior with $d$ between 2.75 and 3.12 and $\theta$ up to 90\degree.~\cite{taylor_geometry_1984,haynes_hydrogen_2008}
  In the main text we chose to use $d$=3.0 and $\theta$=30\degree. We tested the 
  sensitivity of our conclusions to these criteria in Figure~\ref{fig:sensitivity}. 
  The plateau in the percentage reacted monomers is well below 100\% indicating that our
  conclusions hold with even the most lenient criteria.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{hbond_geometry.pdf}
  \caption{We identify hydrogen bonds using geometric criteria based on
  the distance, $d$, between the donor (D) and acceptor (A) atoms as well
  as the angle, $\theta$, between the $\protect\overrightarrow{DH}$ and
  $\protect\overrightarrow{HA}$ vectors (where H is the hydrogen atom)}\label{fig:hbond_geometry}
  \end{figure}

  \begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{sensitivity.pdf}
  \caption{We tested the sensitivity of our conclusions to hydrogen bond
  geometric identification criteria. As our conditions become more lenient
  (higher $d$ and $\theta$), the percentage of reacted monomers increases
  but still plateau's well below 100\%.}\label{fig:sensitivity}
  \end{figure}

  \pagebreak
  \bibliography{Catalysis}

\end{document}

### 2019-10-06 Ben_Manuscripts/stochastic_transport/Draft.tex
MRS comments.

@@
 
+%MRS4: Overall - providing a bit gentler easing into the modeling would help.
+A more clearly articulated overall picture of what the goals of the modeling are.
+Does it have to be perfect?
+Is the main goal just predictive time series, or mechanistic understanding?
+Help people a bit more to understand what success or failure would look like.
+Help make it clear why the specific models are chosen to investigate.
+%MRS4: To what extent can findings be related back to molecular details?
+%MRS4: what are the consequences of the findings?
+
 \title{Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 %MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
+%MRS4: can we turn this into a thesis statement (we find X) rather than a topic statement (we studied X).  Something about the complexity of the models required to get the subdiffusive behavior right?
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   \begin{abstract}
-
   Mathematically modeling complex transport phenomena at the molecular level 
@@
   of parameters based on the solute's radial distance from the closest pore center.
-  Our second model, an adaptation of Markov state models, treats the system
-  as a Markov process where we quantify the transitions between a set of 
-  explicitly defined states. We incorporate the magnitude and temporal correlation
+  Our second model, an adaptation of Markov state models, treats the 
+  %MRS4: I don't think this quite captures what is going on, tried to rephrase.
+  %system as a Markov process, where we quantify the transitions between a set of 
+  %explicitly defined states. 
+  configurational state of the system as a Markov process, each of which has state dependent transport behavior.
+  We 
+  %MRS4: tweaked
+  %incorporate 
+  fit
+  the magnitude and temporal correlation
   of positional fluctuations into each state and transitions between states to gain
@@
   reasonably reproduce MSDs calculated from molecular simulations. The anomalous 
-  diffusion shows superior predictive performance, in many cases exactly reproducing
-  MD results within error. We use the parameters of each model to offer additional mechanistic
+  diffusion shows superior predictive performance, in many cases 
+  %exactly 
+  reproducing
+  MD results
+  %MRS4: added
+  well 
+  within error. 
+  %MRS4: next two sentences seem somewhat repetitive
+  We use the parameters of each model to offer additional mechanistic
   insight. These parameters are important for identifying specific differences in 
@@
   made to LLC membrane monomers in order to increase or reduce selectivity towards a 
-  specific solute.
-
+  specific solute
+  %MRS4: added
+  or class of solutes.
   \end{abstract}
@@
   Mathematical descriptions of transport in complex separations membranes are a powerful 
-  way to understand mechanisms and formulate membrane design principles. The complexity
-  of a model generally parallels the complexity of the transport mechanism at hand, as
-  well as the desired outputs. In dense homogeneous membranes, the solution-diffusion 
+  way to understand mechanisms and formulate membrane design principles. 
+  %MRS4: are there citations for the above, like reviews?
+  The complexity
+  of a model generally parallels the complexity of the transport mechanism at hand, 
+  well as 
+  the transport information the model conveys.
+  %the desired outputs. 
+  In dense homogeneous membranes, the solution-diffusion 
   model can extract diffusion and partition coefficients and has successfully predicted
-  solute transport rates. Analogously, pore-flow models yield predictions of diffusion 
+  solute transport rates. 
+  %MRS4: citation above?
+  Analogously, pore-flow models yield predictions of diffusion 
   coefficients and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
@@
   by attempting to give a more intuitive understanding of how solutes move as a function
-  of their environment, in turn suggesting experiments that should be run.
-
+  of their environment, in turn suggesting experiments that 
+  %should be run.
+  could be performed
   % BJC1: tie this paragraph into above by commenting that highly selective membranes
@@
   % BJC3:maybe change this paragraph to just be examples of highly selective separations, not
-  Facile design of highly selective separations membranes is desirable in numerous
+  %MRS4: below - seems to just be about need for selective membranes, not the design of them.
+  Facile design
+  of highly selective separations membranes is desirable in numerous
   applications. The ability to efficiently separate ions from saline water sources using 
@@
 %  space available to design these types of membranes. 
-  We want to use a molecular model in order to understand how we can leverage the large 
-  chemical space available for LLC monomer design in order to create efficient solute-specific
-  separations. To date, only a limited subset of LLC monomers have been studied in membrane
+  We 
+  %MRS4: proposed change
+  %want to use a molecular model in order to understand how we can leverage the large 
+  %chemical space available for LLC monomer design in order to create efficient solute-specific
+  %separations. 
+  Molecular modeling may make it possible to create efficient solute-specific
+  separation membranes using the available chemical space of LLC monomers.
+  To date, only a limited subset of LLC monomers have been studied in membrane
   applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
-  Even within this small subset, there have been shown selectivities that could not be
+  Even within this small subset, 
+  %there have been shown
+  they have demonstrated selectivities that could not be
   explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
-  Atomistic molecular modeling provides the resolution necessary to identify molecular 
-  interactions that are key to separation mechanisms allowing us to move beyond 
-  traditional Edisonian design.
+  Atomistic molecular modeling 
+  %MRS4
+  %provides 
+  can provide
+  the resolution necessary to identify molecular 
+  interactions that are key to separation mechanisms, allowing us to move beyond 
+  %traditional 
+  %MRS4: above: some would argue lots of design approaches are traditional, not just Edisonian
+  Edisonian design approach.
 
@@
 
+  %MRS4: consider more citations below, when you talk about what researchers have done.
   Researchers have developed a rigorous theoretical foundation for describing the 
@@
   applying the mathematical formalism describing subdiffusive transport to observed
-  solute trajectories. We fit anomalous diffusion models in two ways: First, based 
-  on a single set of parameters. Second, we use a two-state approach incorporating
+  solute trajectories. We fit anomalous diffusion models in two ways: 
+  %MRS4: can you clarify the sentence below?  Probably something like: uses a single set of parameters in the diffusion equations, etc.
+  First, based on a single set of parameters. Second, we use a two-state approach incorporating
   two sets of parameters based on a solute's radial distance from the closest pore center.
@@
   While elegant, pure anomalous diffusion theory may in some cases give only a 
-  qualitative understanding of transport mechanisms. Complex temporal relationships in 
+  qualitative understanding of transport mechanisms. 
+  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
+  %Relating it to molecular scale behavior and examples might help.
+  Complex temporal relationships in 
   between hops may have a significant effect on the average MSD. Inhomogeneity of 
@@
   small set of known states based on the three observed solute trapping mechanisms.
+  %MRS4: but yours assume first order state kinetics as well.
   Standard MSMs assume first order kinetics and are typically applied 
   towards determining equilibrium populations of and the transitions between 
-  various state configurations.~\cite{bowman_using_2009} We extend the framework
-  to include dynamics within states and between jumps. That is we parameterize 
+  various state configurations.~\cite{bowman_using_2009} 
+  %MRS4: this probably needs to be explained more explicitly, that the coordinates of the solute are generated according to the current state. 
+  We extend the framework
+  to include dynamics within states and between jumps. 
+  %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
+  That is we parameterize 
   and incorporate into our model the magnitude and temporal correlation of
@@
   We studied transport of solutes in the H\textsubscript{II} phase using an atomistic
-  molecular model of four pores in a monoclinic unit cell with 10 \% water by weight 
+  molecular model of four pores in a monoclinic unit cell with 10\% water by weight 
   (see Figure~\ref{fig:membrane_structure}). Approximately one third of the water 
   molecules occupy the tail region with the rest near the pore center. We chose to
-  focus our study on the 10 wt \% water system because solutes move significantly 
-  faster than in the 5 wt \% system studied previously. Appropriate stochastic 
+  focus our study on the 10 wt\% water system because solutes move significantly 
+  faster than in the 5 wt\% system studied previously. Appropriate stochastic 
   modeling requires that solutes sample the accessible mechanisms with representative
@@
   to collect ample data. We simulated the system with a time step of 2 fs at a pressure
-  of 1 bar and 300 K controlled by the Parinello-Rahman barostat and the v-rescale 
+  of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and the v-rescale 
   thermostat respectively. We recorded frames every 0.5 ns.
 
-  We considered each system to be equilibrated when the solute partition between the 
-  pore and tail region stopped changing. We excluded data collected before equilibration
-  from our analysis. We plotted the solute partition versus time in Figure~\ref{S-fig:equilibration}
+  We considered each system to be equilibrated when the solute partitioning between the 
+  pore and tail region %stopped changing. 
+  reaches apparent equilibrium.
+  %MRS4: added
+  and use only data after that point in our analysis of solute kinetics.
+  %We excluded data collected before equilibration
+  %from our analysis. 
+  We plot the solute partition versus time in Figure~\ref{S-fig:equilibration}
   of the Supporting Information in order to justify our choice of equilibration times
@@
   % BJC3: x --> z since I'm measuring diffusion in the z direction?
+  %MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x.  
   Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
@@
   where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
-  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. If the underlying 
+  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. 
+  %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
+  If the underlying 
   subdiffusive process is not ergodic, like a pure CTRW, the time averaged MSD becomes
@@
 
-  We believe that solute motion in the system studied here may be consistent with 
+  %MRS4: Tweak
+  %We believe that 
+  The solute motion in the system studied here may be consistent with 
   subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
   the leading process is a CTRW. We observe hopping and trapping which is consistent
-  with a CTRW along with negatively correlated hops which is consistent with FBM.
-
-  One can characterize a CTRW process using the parameters which describe its dwell 
+  with a CTRW, along with negatively correlated hops which is consistent with FBM.
+
+  One can characterize a CTRW process 
+  %using 
+  by 
+  the parameters which describe its dwell 
   time and hop length distributions. We used the \texttt{ruptures} python package in 
@@
     \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
-    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)sin(\pi H)}
+    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
     \label{eqn:flm_autocovariance}
@@
 
+  %MRS4: should be more clear which of the two kinetics scenarios this next assumption applies to
   \subsubsection*{Multiple Dynamical Modes}
@@
   on the solute's radial location. Solutes in mode 1 are in the pore region, defined
+  %MRS4: some justification on why 0.75 vs. any other cutoff.
   as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
@@
 
+  %MRS4: Do you assume Markovian behavior in transitions between the states?  Be explicit.
   \subsubsection*{Simulating Anomalous Diffusion}
 
-  We simulated models with all combinations of dwell and hop length distributions
-  described above, summarized in Table~\ref{table:anomalous_models}. All models 
+  %MRS4: tweaked: otherwise sounds like you simulated all parameters values as well.
+  We simulated models with all combinations of 
+  the types of 
+  dwell and hop length distributions
+  described above, which are summarized in Table~\ref{table:anomalous_models}. All models 
   include correlation between hops.
+  %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
   \begin{table}[!htb]
@@
   decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
-  We reported the time-averaged MSD after time lags 40 \% the length of the trajectory
-  with corresponding 95 \% intervals.
+  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
+  with corresponding 95\% intervals.
   %BJC3: Not sure if 40 % above is too long. I could do 20
-
+  %MRS4: is there some rule of thumb that could be used to justify the choice?
   When simulating 2 mode models, we determined the state sequence based on random 
   draws weighted by the appropriate row of the probability transition matrix. We 
+  %MRS4: not quite sure what you mean by incorporating uncertainty. 
   incorporated uncertainty into transition probabilities by drawing samples from a 
@@
   the count matrix.~\cite{bacallado_bayesian_2009} We drew hops and dwells based on
-  the current state of the system. We used a single Hurst parameter to describe
+  the current state of the system. 
+  %MRS4: you saiid this a couple of paragraphs before. 
+  We used a single Hurst parameter to describe
   correlation between hops, independent of the solute's mode. Ideally, each mode
@@
   simulation algorithms for generating FLM trajectories, however, the algorithm
-  we used sufficiently approximates draws from the marginal distribution and reasonably 
+  we used sufficiently approximates draws from the marginal distribution and 
+  reasonably 
   approximates the correlation structure. We added an empirical correction to enhance
   the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
-  of the Supporting Information).
+  of the Supporting Information
+  %MRS4: added 
+  for validation of the approach 
+  ).
 
@@
   mechanisms observed in our previous work. Therefore, there is no need to subject
+  %MRS4: not clear what dimensionality is being referred to here.
   our trajectories to any reduction in dimensionality. 
@@
 
+  %MRS4: here, be more explicit you are testing the validity of the Markovian approximation on the molecular data.
   We verified the Markovianity of our process by analyzing the transition matrix. An 
@@
 
-  Adding to the standard MSM framework, we attempted to incorporate the dynamics within 
-  each state as well as the dynamics of state transitions. While MSMs are often used to 
-  gauge equilibrium populations of various states, adding dynamics will allow us to  % BJC3 a reference would be good.
+  %MRS4: I mean, you did add it, you didn't just attempt.
+  Adding to the standard MSM framework, 
+  %we attempted to incorporate 
+  incorporate
+  the dynamics of the solute
+  within 
+  %MRS4: tried to be more clear. 
+  each state as well as the dynamics of state transitions, which include the overall configurational state of the solute and it's environments. 
+  While MSMs are often used to 
+  gauge equilibrium populations of various states, adding 
+  %MRS: it's not just ``dynamics'', though, it's a specific subset of the dynamics.  
+  % And one could argue that the MSMs are being added to the dynamics, since the time trace is the desired output, 
+  % rather than the output one usually gets from MSMs.
+  dynamics will allow us to  % BJC3 a reference would be good.
   more accurately simulate solute trajectories. Hence we distinguish our model from 
@@
   drawing subsequent states weighted by the rows of the probability transition matrix
-  corresponding to the particle's current state. Again we incorporated uncertainty into
+  corresponding to the particle's current state. 
+  %MRS4: not quite clear what you mean here by ``incorporated uncertainty''.  Any sort of draws would result in different stochastic processes, which included uncertainty . . . 
+  Again we incorporated uncertainty into
   the rows of the transition matrix by resampling them from a Dirichlet distribution. 
@@
 
-  We believe that solutes in this system can be well-modeled by subordinated fractional
+  %MRS4:  tweaked
+  The evidence suggests
+  %We believe 
+  that solutes in this system can be well-modeled by subordinated fractional
   Brownian motion. The solutes clearly perform jumps after periods of relative immobility
@@
   \end{subfigure}
+  %MRS4: no y axis on inset in c)
   \caption{(a) Urea exhibit hops between periods of entrapment, characteristic of a CTRW. 
@@
   hop. In combination (a) -- (d) support modeling solutes as subordinated fractional Brownian
-  motion. The behavior shown by Urea in this figure is common to all solutes in this study.}\label{fig:anticorrelated_hops}
+  motion. The behavior shown by urea in this figure is common to all solutes in this study.}\label{fig:anticorrelated_hops}
+  %MRS4: are there similar figures in the supporting information.
   \end{figure}
@@
   distributions since it is more general than the Gaussian distribution. We plotted
-  the MLE fits of both on top of Urea's hop length distribution in 
+  the MLE fits of both on top of urea's hop length distribution in 
   Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a better
@@
   the tails, it still has an appreciable probability of making large hops. This could 
-  be a consequence of urea's small profile. Ethylene glycol is a linear chain that can
-  easily become entangled among the alkane tails while urea is planar with its four
-  heavy atoms bonded to a single central atom.
+  be a consequence of urea's 
+  %MRS4: ``small profile'' is vague. Made more concise.
+  %small profile. 
+  relatively small size and rigid shape compared to ethylene glycol.
+  %Ethylene glycol is a linear chain that can
+  %easily become entangled among the alkane tails while urea is planar with its four
+  %heavy atoms bonded to a single central atom.
 
@@
   law tails and higher values of $\lambda$ truncate the distribution at lower
-  dwell times. We paramterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
+  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
   ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
@@
   \end{tabular}
+  %MRS4: more about what the consequences of these results are?
   \caption{To create a 2 mode model, we generated a set of parameters based on solute
@@
   \caption{MSDs generated from realizations of our 1 mode anomalous diffusion models
-  agree well with MD-generated data. When we do not apply an exponential cut-off to the
-  dwell time distribution (sFBM and SFLM), MSDs are underpredicted. Drawing hops from
+  agree well with MD-generated data
+  %MRS4:
+  when using an exponential cutoff (sFBMcut and SFLMcut).
+  When we do not apply an exponential cut-off to the
+  dwell time distribution (sFBM and SFLM), MSDs are underpredicted. 
+  %MRS4: say explicitly which lines on the graph show the next point.
+  Drawing hops from
   a truncated L\'evy stable distribution results in higher MSDs than draws from Gaussians.}\label{fig:anomalous_msds_1mode}
@@
   \caption{MSDs generated from realization of our 2-mode anomalous diffusion model
-  also match well to MD-generated data. The MSD of Urea appears to be underpredicted
+  also match well to MD-generated data. The MSD of urea appears to be underpredicted
   by all model combinations. The MSD of ethylene glycol is predicted well when 
@@
 %  law tails and higher values of $\lambda$ truncate the distribution at lower
-%  dwell times. We paramterized Gaussian ($\mathcal{N}$) and L\'evy stable 
+%  dwell times. We parameterized Gaussian ($\mathcal{N}$) and L\'evy stable 
 %  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
@@
   % spin this paragraph in a different way.
+  %MRS4: can one to training and validation?  Train on 1/2 the data, then see how well it fits the other half?
+  %MRS4: also, you need to be more specific about choosing for WHAT purpose.  Different purposes could imply different models.
   Choosing which model to use for long timescale projections is not entirely obvious
@@
   are tabulated in Table~\ref{table:msddm_params}. 
-
+  %MRS: might this work better visually?  Table in SI, figure here?
   \begin{figure}
@@
   of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
-  Urea and ethylene glycol spend 56 \% and 44 \% of their time in the tails
+  Urea and ethylene glycol spend 56\% and 44\% of their time in the tails
   respectively. Urea's compact and flat structure allows it to more easily 
@@
 
+  %MRS: make it more clear you are still taking about trapping mechanisms here.
   Urea spends the largest fraction of its time associated with sodium ions.
-  It does so 31 \% of the total time while in the tails (state 3) and 21 \%
+  It does so 31\% of the total time while in the tails (state 3) and 21\%
   of the total time while in the pores (state 7). The electron-dense and 
@@
   Ethylene glycol spends the largest fraction of its time hydrogen bonding.
-  It does so 24 \% of the total time while in the tails (state 2) and 32 \% 
+  It does so 24\% of the total time while in the tails (state 2) and 32\% 
   of the total time while in the pores (state 6). The two hydroxyl groups 
@@
   %BJC3: would take ~ 20 hours to simulation 10000 trajectories.
+  %MRS4: state how much it overestimated (1% or 10000%?)
   The MSDDM over-estimates solute MSDs (see Figure~\ref{fig:msddm_performance}). 
@@
 
+  %MRS4: It's not as clear what effect you are talking about until
+  %later, i.e. the fact that the correlation is destroyed by the
+  %state switching.
     The MSDDM overestimates solute MSDs because we simulated each state
@@
 
+%MRS4: be more clear here what mechanistic insight it offers.
   The MSDDM offers mechanistic insight but cannot be used for reliable predictions
@@
   We have tested two different mathematical frameworks for describing solute
-  motion in an H\textsubscript{II} phase LLC membrane. The parameters of each model offer mechanistic insight.
+  motion in an H\textsubscript{II} phase LLC membrane. 
+  %MRS4: added some more specificity. 
+  The values obtained for the parameters when fitting the models to the timeseries data  
+  %The parameters of each model 
+  offer important mechanistic insight on the molecular details of transport.
   Subordinated fractional Brownian and L\'evy motion have a nice theoretical 
@@
   a solute is in or out of the pore region allows us to break down individual
-  solute motion into the two distinct regimes. We showed that solute motion is
+  solute motion into the two distinct regimes and we showed that solute motion is
   clearly restricted while in the tail region. Our Markov state-dependent dynamical
@@
 
-  We believe that our models have moderate predictive power. The anomalous
+  %MRS4: test/train in order to show power?
+  We believe that our models have moderate predictive power. 
+  %MRS4: be more precise on how superior is quantified below.
+  The anomalous
   diffusion model has superior performance to the MSDDM. Both 1 and 2 mode 
@@
   relative dominance in the real system. For example, it is clear that 
-  sodium ion association is primarily responsible for trapping Urea while 
+  sodium ion association is primarily responsible for trapping urea while 
   hydrogen bonding dominates ethylene glycol. If one redesigns an LLC monomer
-  to eliminate one source of trapping, then high selectivities are possible.
+  to eliminate one source of trapping, 
+  %MRS4: by what mechanisms are high selectivities possible?
+  then high selectivities are possible.
 
@@
 
-  \section*{Acknowledgements}
-
+  \section*{Acknowledgments}
+  %MRS: add people who contributed non-author level ideas. 
   %MRS3: add specific info for PRF and GAANN
   %BJC3: I don't know the PRF info. I wrote GAANN as I did on the last paper which is what Rob Davis told me to do
+  %MRS4: I willō track down the PRF grant number (if typical)
   This work was supported in part by the ACS Petroleum Research Fund grant XXXXXX 
@@
 \end{document}
+
+% LocalWords:  solute MSDs solutes solute's LLC BJC nanoporous maginn Lyotropic
+% LocalWords:  micropollutants LLCs amphiphilic mesophases feng Bicontinuous EG
+% LocalWords:  permeability hatakeyama zhou resel selectivities Edisonian CTRW
+% LocalWords:  subdiffusive timescale timescales subdiffusion FBM RWF metzler
+% LocalWords:  jeon neusius pdf Sokolov ony MSD MSMs chodera MSM AcOH URE MeOH
+% LocalWords:  Hbonding hbonds hbond GROMACS berendsen gromacs der spoel hess
+% LocalWords:  wt Na GA carboxylate Parrinello Rahman barostat rescale msd dt
+% LocalWords:  superdiffusive EB sFBM min Hurwitz factoid MLEs autocovariance
+% LocalWords:  evy sFLM FLM sFLMcut Dirichlet saiid fbm Stoev Taqqu MLE TODO SI
+% LocalWords:  vvvv wehmeyer MSMbuilder pyEMMA featurization Phys Chem bayesian
+% LocalWords:  Markovianity MSDDMs MSDDM resampling TBD MSD's CTRWs GCL acf ACH
+% LocalWords:  urea's alkane overlayed SFLMcut underpredicted Gaussians HMM PRF
+% LocalWords:  params msddm timeseries overpredicted GAANN ACS XSEDE ACI PSC
+% LocalWords:  RMACC TOC

### 2019-10-08 Ben_Manuscripts/stochastic_transport/Draft.tex
Initial edits to draft

@@
 
-\title{Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II}
+ Phase Lyotropic Liquid Crystal Membrane}
 %MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
@@
   of parameters based on the solute's radial distance from the closest pore center.
-  Our second model, an adaptation of Markov state models, treats the 
-  %MRS4: I don't think this quite captures what is going on, tried to rephrase.
-  %system as a Markov process, where we quantify the transitions between a set of 
-  %explicitly defined states. 
-  configurational state of the system as a Markov process, each of which has state dependent transport behavior.
-  We 
-  %MRS4: tweaked
-  %incorporate 
-  fit
-  the magnitude and temporal correlation
-  of positional fluctuations into each state and transitions between states to gain
-  further insight and allow us to predict solute MSDs. We show that our models 
-  reasonably reproduce MSDs calculated from molecular simulations. The anomalous 
-  diffusion shows superior predictive performance, in many cases 
-  %exactly 
-  reproducing
-  MD results
-  %MRS4: added
-  well 
-  within error. 
-  %MRS4: next two sentences seem somewhat repetitive
-  We use the parameters of each model to offer additional mechanistic
-  insight. These parameters are important for identifying specific differences in 
-  solute transport behavior. The differences suggest modifications that can be
-  made to LLC membrane monomers in order to increase or reduce selectivity towards a 
-  specific solute
-  %MRS4: added
+  Our second model, an adaptation of Markov state models, treats the configurational
+  state of the system as a Markov process, each of which has state dependent 
+  transport behavior. For each state and transition between states, we parameterized
+  the distribution and temporal correlation structure of positional fluctuations as
+  a means of characterization and to allow us to predict solute MSDs.
+  We show that our models reasonably reproduce MSDs calculated from molecular 
+  simulations. The anomalous diffusion model shows superior predictive performance, 
+  in many cases reproducing MD results well within error. Finally, we use the 
+  parameters of each model to identify specific differences in solute transport
+  behavior which can help suggest modifications that can be made to LLC membrane 
+  monomers in order to increase or reduce selectivity towards a specific solute
   or class of solutes.
+
   \end{abstract}
@@
 
-  % MRS1: I would start with something more central to the content of the paper - how do solutes move in complex separations membranes?
-Let people know right from the start what the paper is about.
-This paragraph should still be in the intro, but start with something that captures the main question of the paper.
-  % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
-  % BJC2: I'm not sure if this is exactly what you meant though
-%  Making sense of solute motion in complex separations membranes is central to 
-%  understanding transport mechanisms and formulating membrane design principles.
-  % MRS3: seems pretty good.
-We can tweak later when turning into text; I don't think that it will really affect the logic of the paper.
-The introduction will be important here to set the stage, but probably more of that will be in the next paragraph.
-
-  Mathematical descriptions of transport in complex separations membranes are a powerful 
-  way to understand mechanisms and formulate membrane design principles. 
-  %MRS4: are there citations for the above, like reviews?
-  The complexity
-  of a model generally parallels the complexity of the transport mechanism at hand, 
-  well as 
-  the transport information the model conveys.
-  %the desired outputs. 
-  In dense homogeneous membranes, the solution-diffusion 
-  model can extract diffusion and partition coefficients and has successfully predicted
-  solute transport rates. 
-  %MRS4: citation above?
-  Analogously, pore-flow models yield predictions of diffusion 
-  coefficients and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
-  Modern single particle tracking approaches take us beyond continuum modeling and 
-  allow us to characterize complex diffusive behavior.~\cite{manzo_review_2015} 
-  At the molecular level, one can use molecular dynamics (MD) simulations to study both
-  single particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
+  Mathematical descriptions of transport in complex separations membranes are 
+  a powerful way to understand mechanisms and formulate membrane design principles. 
+  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
+  The complexity of a model generally parallels the complexity of the transport 
+  mechanism at hand, as well as the transport information the model conveys.
+  In dense homogeneous membranes, the solution-diffusion model can extract 
+  diffusion and partition coefficients and has successfully predicted solute 
+  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
+  models yield predictions of diffusion coefficients and solute transport rates 
+  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
+  tracking approaches take us beyond continuum modeling and allow us to 
+  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
+  level, one can use molecular dynamics (MD) simulations to study both single 
+  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
   All of these approaches facilitate speculation on the molecular origins of separations
   by attempting to give a more intuitive understanding of how solutes move as a function
-  of their environment, in turn suggesting experiments that 
-  %should be run.
-  could be performed
-  % BJC1: tie this paragraph into above by commenting that highly selective membranes
-  % often have complex mechanistic reasons that aren't explained by simpler models
-  % BJC3:maybe change this paragraph to just be examples of highly selective separations, not
-  %MRS4: below - seems to just be about need for selective membranes, not the design of them.
-  Facile design
-  of highly selective separations membranes is desirable in numerous
-  applications. The ability to efficiently separate ions from saline water sources using 
-  membranes has been actively pursued for years in an effort to create potable water for 
-  people in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
+  of their environment, in turn suggesting experiments that could be performed.
+
+  Highly selective separations membranes are desirable in numerous applications. 
+  The ability to efficiently separate ions from saline water sources using membranes 
+  has been actively pursued for years in an effort to create potable water for people 
+  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
   municipal water supplies, there is a need for membranes that can specifically separate
@@
 
-%  Regardless of which LLC phase ones studies, one must contend with the large chemical design
-%  space available to design these types of membranes. 
-  We 
-  %MRS4: proposed change
-  %want to use a molecular model in order to understand how we can leverage the large 
-  %chemical space available for LLC monomer design in order to create efficient solute-specific
-  %separations. 
-  Molecular modeling may make it possible to create efficient solute-specific
-  separation membranes using the available chemical space of LLC monomers.
-  To date, only a limited subset of LLC monomers have been studied in membrane
-  applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
-  Even within this small subset, 
-  %there have been shown
-  they have demonstrated selectivities that could not be
+  Molecular modeling may make it possible to create efficient solute-specific separation
+  membranes using the available chemical space of LLC monomers. To date, only a limited 
+  subset of LLC monomers have been studied in membrane applications.
+  ~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
+  Even within this small subset, they have demonstrated selectivities that could not be
   explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
-  Atomistic molecular modeling 
-  %MRS4
-  %provides 
-  can provide
-  the resolution necessary to identify molecular 
+  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
   interactions that are key to separation mechanisms, allowing us to move beyond 
-  %traditional 
-  %MRS4: above: some would argue lots of design approaches are traditional, not just Edisonian
-  Edisonian design approach.
+  Edisonian design approaches.
 
@@
   of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
-  %BJC3: not sure the following sentence needs to be said.
   The H\textsubscript{II} is a simpler geometry to model than the Q\textsubscript{I} phase.  
@@
   %MRS4: consider more citations below, when you talk about what researchers have done.
+  %BJC4: added citations of prominent anomalous diffusion work
   Researchers have developed a rigorous theoretical foundation for describing the 
   motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
-  The tools introduced by fractional calculus are instrumental to this theory. They
-  allow us to generalize the normally linear diffusion equation to fractional
+  ~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools introduced by 
+  fractional calculus are instrumental to this theory.~\cite{gorenflo_fractional_1997}
+  They allow us to generalize the normally linear diffusion equation to fractional
   derivative orders, providing descriptions of a much more diverse set of behavior.~\cite{klages_anomalous_2008}
@@
   A CTRW is characterized by a distribution of hop lengths and dwell times, 
-  where each each hop is characterized by independent random draws from 
+  where trajectories are characterized by independent random draws from 
   each distribution.\cite{montroll_random_1965} FBM is common in crowded,
@@
 
-% BJC3: omitted because too rigid. Ergodicity is hard to prove with 24 solute trajectories.
-%  \begin{figure}
-%  \centering
-%  \includegraphics[width=0.7\textwidth]{subdiffusion_decision_tree.pdf}
-%  \caption{This decision tree, adapted from Meroz and Sokolov~\cite{meroz_toolbox_2015},
-%  can be used to isolate potential subdiffusive transport mechanisms based on 
-%  single solute trajectories.}\label{fig:decision_tree}
-%  \end{figure}
-
-  % BJC2: moved this from below
   Our first modeling approach is based on the anomalous diffusion literature, 
@@
   %MRS4: can you clarify the sentence below?  Probably something like: uses a single set of parameters in the diffusion equations, etc.
-  First, based on a single set of parameters. Second, we use a two-state approach incorporating
-  two sets of parameters based on a solute's radial distance from the closest pore center.
+  %BJC4: see if below helps.
+  %First, based on a single set of parameters. 
+  First, we parameterized solute motion using a single set of parameters fit
+  to a hypothesized anomalous diffusion model. Second, we use a two-state approach
+  extracting two sets of model parameters calculated based on a solute's radial
+  distance from the closest pore center.
 
@@
   %Relating it to molecular scale behavior and examples might help.
+  %BJC4: mention ageing
+  %BJC4: ?
   Complex temporal relationships in 
@@
   small set of known states based on the three observed solute trapping mechanisms.  
-  %MRS4: but yours assume first order state kinetics as well.
-  Standard MSMs assume first order kinetics and are typically applied 
-  towards determining equilibrium populations of and the transitions between 
-  various state configurations.~\cite{bowman_using_2009} 
-  %MRS4: this probably needs to be explained more explicitly, that the coordinates of the solute are generated according to the current state. 
-  We extend the framework
-  to include dynamics within states and between jumps. 
+  Standard MSMs are typically applied towards determining equilibrium populations
+  of and the transitions between various state configurations.~\cite{bowman_using_2009} 
+  %MRS4: this probably needs to be explained more explicitly, that the coordinates 
+  %of the solute are generated according to the current state. 
+  %BJC4: made more explicit.
+  %We extend the framework
+  %to include dynamics within states and between jumps. 
+  We extend the framework to include state-dependent fluctuations and correlations in 
+  solute position. 
   %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
-  That is we parameterize 
-  and incorporate into our model the magnitude and temporal correlation of
-  fluctuations in solute position while in each state as well as during transitions
-  to different states. 
-  %Temporal correlation in position has a significant influence on 
-  %a solute's mean squared displacement.
+  %BJC4: rephrased
+%  That is we parameterize 
+%  and incorporate into our model the magnitude and temporal correlation of
+%  fluctuations in solute position while in each state as well as during transitions
+%  to different states. 
+  That is the magnitudes of a solute's fluctuations from its average trapped 
+  position and the degree of correlation with its previous fluctuations is 
+  defined by the parameters of its current state.
 
@@
   %BJC3: need to decide value in long term projections
-
-%  If we can reproduce the MD MSDs within reason
-%  then we can use the parameters of our model to gain additional mechanistic insight.
-%  
-      %MRS: do the solutes also have some diversity of mechanisms (that were observed previously?)
-    %BJC1: Yes. Need to put following into words
-    %BJC1: Ranking of time spent in pore region: AcOH > EG > URE > MeOH  (spans 4th most to 3rd least)
-    %BJC1: All have high hop frequency which is consistent with fast motion
-    %BJC1: Hbonding: Urea barely hbonds. AcOH and EG hbond a lot. AcOH has highest hbond lifetime of all 20 solutes. MeOH on par with all other simple alcohols
-    %BJC1: Sodium Association: Urea coordinates with sodium the most of all 20 solutes. AcOH, EG, MeOH spread out of rest of range. Lifetime similar
 
@@
   We considered each system to be equilibrated when the solute partitioning between the 
-  pore and tail region %stopped changing. 
-  reaches apparent equilibrium.
-  %MRS4: added
-  and use only data after that point in our analysis of solute kinetics.
-  %We excluded data collected before equilibration
-  %from our analysis. 
-  We plot the solute partition versus time in Figure~\ref{S-fig:equilibration}
-  of the Supporting Information in order to justify our choice of equilibration times
-  for each solute.
+  pore and tail region reached apparent equilibrium and use only data after that point
+  in our analysis of solute kinetics. We plotted the solute partition versus time in
+  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify 
+  our choice of equilibration times for each solute.
 
@@
   % BJC3: x --> z since I'm measuring diffusion in the z direction?
-  %MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x.  
+  % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
+  % BJC4: I think it'll be less confusing to me writing it to change it to z. Is it worth
+  % explicitly stating that z is the positional coordinate.
   Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
@@
   \begin{equation} 
-  \langle x^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
+  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
   \label{eqn:msd_form}
@@
 
-  %MRS: describe the physical situations in which one would want to choose each of these ways of calculating the MSD.
-  %BJC1: For determining ergodicity. Ensemble for determining anomalous exponent. Not sure I'll use ensemble MSD
-
-%  We analyzed both the ensemble-averaged and time-averaged MSDs of the simulated
-%  trajectories. The ensemble-averaged MSD measures the displacement of a particle 
-%  from its initial position~\cite{meroz_toolbox_2015} and can be written as
-%  \begin{equation}
-%  \langle x^2(t) \rangle = \langle x(t) - x(0) \rangle^2
-%  \label{eqn:ensemble_msd}
-%  \end{equation}
-%%	\item The average MSD calculated in this way recovers the form of
-%%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
-%  The time-averaged MSD eliminates initial position dependence by measuring all
-%  possible displacements over time lag $\tau$ and can be written as:
-%  \begin{equation}
-%  \overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
-%  \end{equation}
-%  where T is the length of the trajectory~\cite{meroz_toolbox_2015}.
-
   %BJC3: removed ensemble MSD because it's not used
@@
   \begin{equation}
-  \overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
+  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
   \end{equation}
@@
   %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
-  If the underlying 
-  subdiffusive process is not ergodic, like a pure CTRW, the time averaged MSD becomes
-  linear.~\cite{meroz_toolbox_2015}
-
-%  We determined the ergodicity of the solute trajectories using the ergodicity breaking
-%  parameter~\cite{cherstvy_anomalous_2013}:
-%  %First, we tested whether the increments of the process were stationary using the augmented Dickey-Fuller test.
-%  \begin{equation}
-%  EB = \lim_{T \to \infty} \frac{\bigg(\bigg\langle \overline{x^2(T)}^2 \bigg\rangle - \bigg\langle \overline{x^2(T)} \bigg\rangle^2\bigg)}{\bigg\langle \overline{x^2(T)} \bigg\rangle^2}
-%  \end{equation}
-%  Simply stated, $EB$ quantifies the variance or heterogeneity in the time averaged
-%  MSD generated from independent trajectories after ample time has passed. For 
-%  ergodic systems, $EB=0$.
-
-  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
-  % MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
-  % BJC1: modified this paragraph to parallel the flow chart. I'm still not sure the
-  % best place for this. It seems like it belongs in the discussion, but I need to 
-  % justify the choice in model so I can write the methods about the chosen models
-  % BJC2: Perhaps just say that we think it's sFBM and move the proof to discussion.
+  %BJC4: reworded, defined ergodicity (usually called 'weak' ergodicity breaking in literature) and
+  % explained why it's not important for this study.
+  In a pure CTRW, for example, the power law distribution of trapping times leads to
+  weak ergodicity breaking. The time-averaged MSD is linear while the ensemble averaged
+  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
+  law trapping behavior, the time between hops diverges so there is no characteristic
+  measurement time scale of solute motion. In fact, as measurement time increases, the 
+  MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
+  with trapping times on the order of the measurement time get incorporated into the 
+  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
+  because we it is a more statistically robust measure of the average distance a solute
+  travels over time versus the ensemble average. Although theoretically possible, we do
+  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
+  with higher precision using the dwell time distributions as described below.
+
+%  of the process is exhibits weak ergodicity breaking due to 
+%  If the underlying subdiffusive process is not ergodic, like a pure CTRW, the time
+%  averaged MSD becomes linear.
+
   \subsubsection*{Subordinated Fractional Brownian Motion}
 
-  %MRS4: Tweak
-  %We believe that 
   The solute motion in the system studied here may be consistent with 
@@
 
-  One can characterize a CTRW process 
-  %using 
-  by 
-  the parameters which describe its dwell 
+  One can characterize a CTRW process by the parameters which describe its dwell 
   time and hop length distributions. We used the \texttt{ruptures} python package in 
@@
   %MRS4: should be more clear which of the two kinetics scenarios this next assumption applies to
-  \subsubsection*{Multiple Dynamical Modes}
+  %BJC4: changed title to clarify that this is anomalous diffusion
+  \subsubsection*{Multiple Anomalous Diffusion Regimes}
 
@@
   %MRS4: some justification on why 0.75 vs. any other cutoff.
+  %BJC4: I justified sentence after next. Is there something more I should say? 
   as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
@@
   For the two mode model, we defined a transition matrix describing the rate at
-  which solutes moved between the tail and pore region. To do so, we populated a
-  2$\times$2 count matrix by incrementing the appropriate entry by 1 each time step. 
+  which solutes moved between the tail and pore region. We assumed Markovian transitions
+  between modes, meaning each transition had no memory of previously visited modes. 
+  We populated a 2$\times$2 count matrix by incrementing the appropriate entry by 1 each time step. 
   For example, if we observed the solute in the tails followed by a transition to 
@@
   %MRS4: Do you assume Markovian behavior in transitions between the states?  Be explicit.
+  %BJC4: Yes, added sentence directly after thesis above
+
   \subsubsection*{Simulating Anomalous Diffusion}
 
-  %MRS4: tweaked: otherwise sounds like you simulated all parameters values as well.
-  We simulated models with all combinations of 
-  the types of 
-  dwell and hop length distributions
-  described above, which are summarized in Table~\ref{table:anomalous_models}. All models 
-  include correlation between hops.
+  We simulated models with all combinations of the types of dwell and hop length
+  distributions described above, which are summarized in Table~\ref{table:anomalous_models}.
+  All models include correlation between hops.
   %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
@@
   % BJC3: will need to modify this text to reflect different lengths of simulations
-  For each solute, we simulated 10000 anomalous diffusion trajectories of length $T_{sim}$ in
-  order to directly compare our model's predictions to MD simulations. $T_{sim}$ varied due to
-  differing solute equilibration times. We constructed trajectories by simulating 
-  sequences of dwell times and correlated hop lengths generated based on
-  parameters randomly chosen from our bootstrapped parameter distributions. We 
-  propagated each trajectory until the total time equaled or exceeded $T_{sim}~ \mu$s, then
-  truncated the last data point so that the total time exactly equaled $T_{sim}~ \mu$s since
-  valid comparisons are only possible between fixed length sFBM simulations. The
-  power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
-  decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
+  For each solute, we simulated 10000 anomalous diffusion trajectories of length
+  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
+  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
+  trajectories by simulating sequences of dwell times and correlated hop lengths
+  generated based on parameters randomly chosen from our bootstrapped parameter 
+  distributions. We propagated each trajectory until the total time equaled or 
+  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
+  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
+  between fixed length sFBM simulations. 
+  % BJC4: removed following sentence because I talk about aging above
+  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
+  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
   We reported the time-averaged MSD after time lags 40\% the length of the trajectory
@@
   %MRS4: not quite sure what you mean by incorporating uncertainty. 
+  %BJC4: The Dirichlet distribution basically perturbs the transition probabilities
+  % by an amount proportional to the number of observations. So things that don't
+  % get transition to/from frequently will have higher uncertainty. Output of 
+  % draw form Dirichlet distribution sums to 1. It doesn't really change the results
+  % much but I think it's good practice. In the 2D case, it is just a beta distribution
   incorporated uncertainty into transition probabilities by drawing samples from a 
@@
   the current state of the system.
-  %MRS4: you saiid this a couple of paragraphs before. 
-  We used a single Hurst parameter to describe
-  correlation between hops, independent of the solute's mode. Ideally, each mode
-  would have its own Hurst parameter, but we did not observe enough long sequences
-  of uninterrupted time spent in each mode with which to generate robust
-  autocorrelation functions.
+
+  %BJC4: already said this earlier
+%  We used a single Hurst parameter to describe
+%  correlation between hops, independent of the solute's mode. Ideally, each mode
+%  would have its own Hurst parameter, but we did not observe enough long sequences
+%  of uninterrupted time spent in each mode with which to generate robust
+%  autocorrelation functions.
 
@@
   we used sufficiently approximates draws from the marginal distribution and 
-  reasonably 
-  approximates the correlation structure. We added an empirical correction to enhance
-  the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
-  of the Supporting Information
-  %MRS4: added 
-  for validation of the approach 
-  ).
+  reasonably approximates the correlation structure. We added an empirical correction
+  to enhance the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
+  of the Supporting Information for validation of the approach).
 
@@
   In this work, we define a total of 8 discrete states based on the 3 trapping
-  mechanisms observed in our previous work. Therefore, there is no need to subject
-  %MRS4: not clear what dimensionality is being referred to here.
-  our trajectories to any reduction in dimensionality. 
-  %However, we do adopt the
-  %validation techniques used in the packages mentioned above. 
-  The states we've 
-  chosen include all combinations of trapping mechanisms in the pore and out of
-  the pore (see Table~\ref{table:states}). We use the same radial cut-off (0.75 nm)
-  as in the anomalous diffusion model to differentiate the pore and tail region. 
-  These state choices assume that there are no significant kinetic effects resulting
-  from solute conformational changes or pore size fluctuations, an assumption that
-  may be relaxed in future work.
+  mechanisms observed in our previous work. Therefore, there is no need to 
+  apply any algorithmic approaches to identify and decompose our system into 
+  discrete states. The states we have chosen include all combinations of trapping
+  mechanisms in the pore and out of the pore (see Table~\ref{table:states}). We use
+  the same radial cut-off (0.75 nm) as in the anomalous diffusion model to differentiate
+  the pore and tail region. These state choices assume that there are no significant
+  kinetic effects resulting from solute conformational changes or pore size fluctuations,
+  an assumption that may be relaxed in future work.
 
@@
 	  \centering
-      %MRS3: tweaked formatting, change back if you want!
-      %BJC3: I don't like the centering much
 	  \begin{tabular}{|l|l|}
@@
 
-  % BJC: does it make sense to use Dirichlet Process as a conjugate prior for
-  % getting error on transition matrix?
-  % BJC1: aha yes! \cite{bacallado_bayesian_2009}
-
   We constructed the state transition probability matrix, $T$, based on observed solute trajectories.
@@
   %MRS4: here, be more explicit you are testing the validity of the Markovian approximation on the molecular data.
-  We verified the Markovianity of our process by analyzing the transition matrix. An 
-  important condition of a Markov process is the satisfaction of detailed balance:
+  %BJC4: Tried to clarify in thesis statement. Let me know if you think it needs more
+  We verified the Markovianity of state transitions observed in our simulations 
+  by analyzing the empirically measured transition matrix. An important condition
+  of a Markov process is the satisfaction of detailed balance:
   \begin{equation}
@@
   transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
-  test is to verify that $T$ holds up to a coarser time scale.~\cite{swope_describing_2004}
-  We verified these properties in Section~\ref{S-section:markov_validation} of the 
-  Supporting Information.
+  test is to verify that $T$ holds up to coarser time scales. As long as solutes
+  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
+  with time.~\cite{swope_describing_2004} We verified these properties 
+  in Section~\ref{S-section:markov_validation} of the Supporting Information.
 
@@
 
-  %MRS4: I mean, you did add it, you didn't just attempt.
-  Adding to the standard MSM framework, 
-  %we attempted to incorporate 
-  incorporate
-  the dynamics of the solute
-  within 
-  %MRS4: tried to be more clear. 
-  each state as well as the dynamics of state transitions, which include the overall configurational state of the solute and it's environments. 
-  While MSMs are often used to 
-  gauge equilibrium populations of various states, adding 
-  %MRS: it's not just ``dynamics'', though, it's a specific subset of the dynamics.  
+  Adding to the standard MSM framework, we incorporate the dynamics of the solutes
+  within each state as well as the dynamics of state transitions, which include the
+  overall configurational state of the solute and it's environments. 
+  While MSMs are often used to gauge equilibrium populations of various states, adding 
+  %MRS4: it's not just ``dynamics'', though, it's a specific subset of the dynamics.  
   % And one could argue that the MSMs are being added to the dynamics, since the time trace is the desired output, 
   % rather than the output one usually gets from MSMs.
-  dynamics will allow us to  % BJC3 a reference would be good.
+  %BJC4: made more specific with 'state-dependent dynamics' instead of just 'dynamics'
+  %BJC4: confusion here
+  state-dependent dynamics will allow us to
   more accurately simulate solute trajectories. Hence we distinguish our model from 
@@
   corresponding to the particle's current state. 
-  %MRS4: not quite clear what you mean here by ``incorporated uncertainty''.  Any sort of draws would result in different stochastic processes, which included uncertainty . . . 
+  %MRS4: not quite clear what you mean here by ``incorporated uncertainty''.  Any sort 
+  % of draws would result in different stochastic processes, which included uncertainty . . . 
   Again we incorporated uncertainty into
@@
 
-  % BJC: need to add some validation of Markovian behavior and time step choice.
-
   \section{Results and Discussion}
 
-% BJC3: Don't think this section is needed
-%  \subsection{Molecular Dynamics Simulations}\label{section:MD_simulations}
-%  
-%  The MSDs for of the solutes calculated from 5 $\mu s$ MD simulation trajectories
-%  are shown in Figure TBD.
-%  \begin{itemize}
-%    %MRS: probably option 1.
-%    \item 2 options for a figure:
-%    \item 1) 2 panels: 1st panel: bar chart with final MSD value + error bars. 2nd panel: a selected MSD curve
-%    \item 2) 1 panel. All MSD curves. Overlapping errors might look bad
-%  \end{itemize}
-%  
-%  %MRS: I'm not sure where the below is different from what was found in the previous study (i.e MSD's).
-%  % BJC1: move to supporting if included
-%%  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
-%%  previous work.
-%%  \begin{itemize} 
-%%    \item The extent to which each trapping mechanism influences each solute is
-%%  	depicted graphically in Figure TBD.
-%%    \item Same types of figures from transport paper:
-%%    \item Fraction participating in hydrogen bonds, fraction associated, fraction
-%%    in the tails.
-%%    \item Lifetimes of hbonds and sodium associations?
-%%  \end{itemize}
-%
-%  Methanol and acetic acid are not fully equilibrated, therefore we did not use them
-%  to test our models.
-
   \subsection{Anomalous Diffusion Modeling}\label{section:sFBM}
 
-  %MRS4:  tweaked
-  The evidence suggests
-  %We believe 
-  that solutes in this system can be well-modeled by subordinated fractional
-  Brownian motion. The solutes clearly perform jumps after periods of relative immobility
+  The evidence suggests that solutes in this system can be well-modeled by 
+  subordinated fractional Brownian motion. The solutes clearly perform jumps after periods of relative immobility
   (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
@@
   \end{subfigure}
-  %MRS4: no y axis on inset in c)
   \caption{(a) Urea exhibit hops between periods of entrapment, characteristic of a CTRW. 
@@
   %MRS4: are there similar figures in the supporting information.
+  %BJC4: no but I can make them
   \end{figure}
@@
   the tails, it still has an appreciable probability of making large hops. This could 
-  be a consequence of urea's 
-  %MRS4: ``small profile'' is vague. Made more concise.
-  %small profile. 
-  relatively small size and rigid shape compared to ethylene glycol.
+  be a consequence of urea's relatively small size and rigid shape compared to ethylene glycol.
   %Ethylene glycol is a linear chain that can
@@
   \caption{To create a 1 mode model for each solute, we parameterized a pure power
-  law ($P(\alpha_d)$) and a truncated power law $P_T(\alpha_d, \lambda)$ distribution 
+  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
   to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
@@
 
-  %BJC3: wondering if I should cut these plots off at 20 % of total equilibrated simulation time instead of 40.
   \begin{figure}
@@
   \caption{MSDs generated from realizations of our 1 mode anomalous diffusion models
-  agree well with MD-generated data
-  %MRS4:
-  when using an exponential cutoff (sFBMcut and SFLMcut).
-  When we do not apply an exponential cut-off to the
-  dwell time distribution (sFBM and SFLM), MSDs are underpredicted. 
-  %MRS4: say explicitly which lines on the graph show the next point.
-  Drawing hops from
-  a truncated L\'evy stable distribution results in higher MSDs than draws from Gaussians.}\label{fig:anomalous_msds_1mode}
+  agree well with MD-generated data when using an exponential cutoff (sFBMcut and SFLMcut).
+  When we do not apply an exponential cut-off to the dwell time distribution (sFBM 
+  and SFLM), MSDs are underpredicted. Drawing hops from a truncated L\'evy stable 
+  distribution results in higher MSDs than draws from Gaussians (sFLM and sFLMcut).}\label{fig:anomalous_msds_1mode}
   \end{figure}
@@
   are tabulated in Table~\ref{table:msddm_params}. 
-  %MRS: might this work better visually?  Table in SI, figure here?
+  %MRS4: might this work better visually?  Table in SI, figure here?
+  %BJC4: like a bar plot?
   \begin{figure}
@@
 
-  %MRS: make it more clear you are still taking about trapping mechanisms here.
-  Urea spends the largest fraction of its time associated with sodium ions.
+  %MRS4: make it more clear you are still taking about trapping mechanisms here.
+  Urea spends the largest fraction of its time trapped via association with sodium ions.
   It does so 31\% of the total time while in the tails (state 3) and 21\%
@@
 
-  Ethylene glycol spends the largest fraction of its time hydrogen bonding.
-  It does so 24\% of the total time while in the tails (state 2) and 32\% 
-  of the total time while in the pores (state 6). The two hydroxyl groups 
+  Ethylene glycol spends the largest fraction of its time trapped in a hydrogen
+  bonded state. It does so 24\% of the total time while in the tails (state 2)
+  and 32\% of the total time while in the pores (state 6). The two hydroxyl groups 
   of ethylene glycol readily donate their hydrogen atoms to the carboxylate
@@
   %MRS4: state how much it overestimated (1% or 10000%?)
-  The MSDDM over-estimates solute MSDs (see Figure~\ref{fig:msddm_performance}). 
+  The MSDDM over-estimates solute MSDs by 200--300 \% (see Figure~\ref{fig:msddm_performance}). 
   We simulated 1000 trajectories as described in Section~\ref{method:MSMs} then

### 2019-10-08 Ben_Manuscripts/stochastic_transport/figures/msd_comparison.py

@@ -66,6 +66,9 @@ sys = file_rw.load_object('%s/forecast_%s_%dstate.pl' % (directory, res, nmodes)
 dwell_dist = ['Power Law', 'Power Law Exponential Cutoff', 'Power Law', 'Power Law Exponential Cutoff']
 hop_dist = ['Gaussian', 'Gaussian', 'Levy', 'Levy']
 
+dwell_dist = ['Power Law Exponential Cutoff']
+hop_dist = ['Levy']
+
 # names here will appear in legend
 abbreviations = {'Power Law Gaussian': 'sFBM', 'Power Law Exponential Cutoff Gaussian': 'sFBMcut', 'Power Law Levy': 'sFLM', 'Power Law Exponential Cutoff Levy': 'sFLMcut'}
 
@@ -136,7 +139,8 @@ for i, dists in enumerate(zip(dwell_dist, hop_dist)):
 		
 	labels.append(abbrev)
 
-plt.legend(labels, loc=0, fontsize=14)
+#plt.legend(labels, loc=0, fontsize=14)
 plt.tight_layout()
-plt.savefig('%dmode_msd_comparison_%s.pdf' % (nmodes,res))
+plt.savefig('toc_msd.png')
+#plt.savefig('%dmode_msd_comparison_%s.pdf' % (nmodes,res))
 plt.show()

### 2019-10-08 LLC_Membranes/timeseries/forecast_ctrw.py

@@ -64,6 +64,8 @@ def initialize():
     # parser.add_argument('-radius', default=1, type=float, help='Radius of pores. Anything greater than this distance'
     #                     'from the pore center will not be included in calculation')
 
+    parser.add_argument('-suffix', '--save_suffix', default=None, help='If not None, add this suffix to save name')
+
     return parser
 
 
@@ -133,7 +135,13 @@ if __name__ == "__main__":
 
         sys.t = None  # save memory in pickled file this info is no longer needed. Can write function to reload
         sys.com = None
-        file_rw.save_object(sys, 'forecast_%s_%dstate.pl' % (fit['residue'], sys.nmodes))
+
+        savename = 'forecast_%s_%dstate' % (fit['residue'], sys.nmodes)
+        if args.save_suffix is not None:
+            savename += args.save_suffix
+        savename += '.pl'
+
+        file_rw.save_object(sys, savename)
 
     # sys.fit_distributions(nbins=fit['bins'], nboot=10, plot=True, show=True, save=True,
     #                       dwell_distribution=fit['dwell_distribution'], hop_distribution=fit['hop_distribution'])

### 2019-10-08 LLC_Membranes/timeseries/truncated_levy_database.py

@@ -19,7 +19,7 @@ from LLC_Membranes.timeseries.flm_sim_params import TruncateLevy
 alphas = np.linspace(1, 2, 10)
 H = np.linspace(0.0, 0.5, 11)
 trunc = np.linspace(1, 100, 10)
-scale = 0.032
+scale = 0.045
 nrealizations = 10
 load = False
 append = True

### 2019-10-09 Ben_Manuscripts/stochastic_transport/Draft.tex
Additions to intro

@@
 
-  Molecular modeling may make it possible to create efficient solute-specific separation
+  Molecular modeling may make it possible to efficiently create solute-specific separation
   membranes using the available chemical space of LLC monomers. To date, only a limited 
   subset of LLC monomers have been studied in membrane applications.
-  ~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
+  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
   Even within this small subset, they have demonstrated selectivities that could not be
@@
   of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
-  The H\textsubscript{II} is a simpler geometry to model than the Q\textsubscript{I} phase.  
+  The H\textsubscript{II} phase is a simpler geometry to model than the Q\textsubscript{I} phase.  
   In general, we observed subdiffusive transport behavior characterized by intermittent hops 
@@
   motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
-  ~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools introduced by 
+  \cite{metzler_random_2000,bouchaud_anomalous_1990} The tools introduced by 
   fractional calculus are instrumental to this theory.~\cite{gorenflo_fractional_1997}
@@
   The theory is frequently used to describe single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
+  %BJC4: consider rewording sentence below
   A CTRW is characterized by a distribution of hop lengths and dwell times, 
@@
 
+  %BJC4: should I mention which anomalous subdiffusion model we chose? 
   Our first modeling approach is based on the anomalous diffusion literature, 
@@
 
+  %BJC4: might want to change the theme of this paragraph to something like: 
+  % Anomalous diffusion can help uncover mechanisms. Once we know mechanisms, we 
+  % can define them as states and use the MSDDM.
   While elegant, pure anomalous diffusion theory may in some cases give only a 
@@
   position and the degree of correlation with its previous fluctuations is 
-  defined by the parameters of its current state.
-
-  In this work we apply the two modeling approaches in order to predict the long
-  timescale behavior of the four fastest moving solutes studied in our previous work.
+  defined by the parameters of its current state. To distinguish our approach from
+  standard MSMs, we have named it the Markov state-dependent dynamical model (MSDDM).
+  %BJC4: Added name of our modeling approach in last sentence
+
+  %BJC4: making goals more explicit
+  The success of our modeling approaches can be defined in two ways. First, if we
+  can closely reproduce solute MSDs measured from MD simulations with realizations
+  of our models, then it is likely that the model sufficiently captures solute 
+  dynamics and can be used in a predictive capacity. Even if a model fails to 
+  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
+  The second measure of success is by analysis of the parameters defining each 
+  model. The parameters themselves should provide clues that help explain solute 
+  behavior in a coherent way. A model that successfully reproduces MD MSDs, but 
+  with nonsensical parameters has severely diminished value.
+
+  % BJC4: new paragraph
+  The goal of this work is not to definitively determine which modeling approach
+  is better but to evaluate their performance independently because they both
+  have potential value dependent on one's research goals. The anomalous subdiffusion
+  approach provides a systematic way to compare the dynamical behavior of different
+  solutes based solely on the time series of their center of mass positions. The process
+  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
+  since it requires a thorough analysis of solute time series behavior. One can then
+  screen different solutes, compare the fit model parameters and relate them back to 
+  differences in solute size and chemical composition. The MSDDM characterizes 
+  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
+  while in each trapped state as well as the equilibrium occupation of each trapping state.
+  It is possible to use the two models in tandem, the anomalous diffusion model to
+  identify mechanisms, and the MSDDM to characterize mechanisms.
+
+  %BJC4: missing something about predictive capabilities
+
+  We evaluate the two modeling approaches by using them to characterize the dynamical
+  behavior of the four fastest moving solutes studied in our previous work.
   Specifically, we study methanol, urea, ethylene glycol and acetic acid. In addition
@@
   these solutes have a range of chemical functionality and experience each of the 
-  three trapping mechanisms to different degrees. It is our goal to reproduce
-  the mean squared displacements (MSDs) exhibited by each solute on MD timescales and
-  then to project the long-term dynamics of each solute. We can gain further
-  mechanistic insight by studying the parameters of each model. 
+  three trapping mechanisms to different extents.
+
+%  It is our goal to reproduce
+%  the mean squared displacements (MSDs) exhibited by each solute on MD timescales and
+%  then to project the long-term dynamics of each solute. We can gain further
+%  mechanistic insight by studying the parameters of each model. 
   %BJC3: need to decide value in long term projections
@@
   %MRS4: state how much it overestimated (1% or 10000%?)
+  %BJC4: added percentages. Is it redundant since I already said how many time
   The MSDDM over-estimates solute MSDs by 200--300 \% (see Figure~\ref{fig:msddm_performance}). 
@@
   %BJC3: 2.2 and 3.3 x higher than MD to be exact
-  calculated their MSDs. The MSD of urea and ethylene glycol are about 2 and 3 times
+  calculated their MSDs. The MSDs of urea and ethylene glycol are about 2 and 3 times
   higher than MD simulations respectively.
@@
   %state switching.
-  The MSDDM overestimates solute MSDs because we simulated each state
-  sequence independently. Although correlation exists within each
+  %BJC4: modified thesis
+  The MSDDM overestimates solute MSDs because correlation is lost
+  every time a state switch occurs. Although correlation exists within each
   sequence, there is no memory of the previous state or state transition 
@@
   As we increase the self-transition probability, $T_{ii}$, the simulated MSD 
-  decreases. Longer dwell times in each state allow us to more accurately
+  decreases. Consequently longer dwell times in each state allow us to more accurately
   simulate the negative correlation that we observe in MD.
@@
 
-%MRS4: be more clear here what mechanistic insight it offers.
+  % MRS4: be more clear here what mechanistic insight it offers.
+  % BJC4: added a couple sentences after thesis
   The MSDDM offers mechanistic insight but cannot be used for reliable predictions
-  of solute MSDs. It may be suitable for processes with rarer transitions between 
-  states. If we can further reduce the state-space of our models, the MSDDM
-  may have better predictive success, but we lose mechanistic detail.
+  of solute MSDs. We can obtain a detailed picture of dynamics within each state in
+  terms of the magnitude of their fluctuations and correlation with previous 
+  motion. Unfortunately correlation between adjacent same-state sequences is lost
+  with our model which causes the MSDs to be significantly over-predicted. The MSDDM
+  may be suitable for processes with rarer transitions between states. If we can 
+  further reduce the state-space of our models, it may have better predictive success,
+  but we lose mechanistic detail.
 
@@
 
-  % MRS1: will want to make a statement about whether these approaches
-  % are together good enough for predictive purposes, and if not,
-  % explore what else should be done in the future.
-  % BJC2: It seems like it would be hard to make say these can be used
-  % for prediction without experimental confirmation of the trends that we observe.
-
   We have tested two different mathematical frameworks for describing solute
-  motion in an H\textsubscript{II} phase LLC membrane. 
-  %MRS4: added some more specificity. 
-  The values obtained for the parameters when fitting the models to the timeseries data  
-  %The parameters of each model 
-  offer important mechanistic insight on the molecular details of transport.
+  motion in an H\textsubscript{II} phase LLC membrane. The values obtained for
+  the parameters when fitting the models to the time series data offer important
+  mechanistic insight on the molecular details of transport.
   Subordinated fractional Brownian and L\'evy motion have a nice theoretical 
@@
   sodium ion association is primarily responsible for trapping urea while 
-  hydrogen bonding dominates ethylene glycol. If one redesigns an LLC monomer
+  hydrogen bonding dominates ethylene glycol. If one re-designs an LLC monomer
   to eliminate one source of trapping, 

### 2019-10-14 Ben_Manuscripts/catalysis/Supporting_Information.tex
Tandem catalysis SI updates

@@
 
+  We extrapolated the final number of reacted catalytic groups by fitting a
+  plateauing function of the form:
+  \begin{equation}
+  f(x) = M(1 - x^{-a})
+  \label{eqn:plateau}
+  \end{equation}
+  where $M$ and $a$ are the asymptotic maximum function value and the rate of
+  decay respectively. We believe this type of fit is necessary because the 
+  number of hydrogen bond "reactions" continues to grow slowly over time even
+  after long plateaus (see Figure~\ref{fig:reacted_all}).
+
+  There are multiple regimes of growth in the number of hydrogen bond surrogate
+  reactions. Since we are interested in the asymptotic value, $M$, of the plateau,
+  we fit Equation~\ref{eqn:plateau} to the average growth curve starting after
+  40 ns where the percent reacted head groups versus the log of time becomes
+  consistently linear (see Figure~\ref{fig:loglog}).
+
+%  Because the system is very slowly approaching a plateau, we found that 
+%  an $x^{-a}$ power law dependence in Equation~\ref{eqn:plateau} provided 
+%  a better fit to the data than an exponential dependence ($e^{-ax}$) 
+%  (see Figure~\ref{fig:fit_comparison}).
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{reacted_all.pdf}
+  \caption{}\label{fig:reacted_all}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{loglog.pdf}
+  \caption{}\label{fig:loglog}
+  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{fit_comparison.pdf}
+%  \caption{}\label{fig:fit_comparison}
+%  \end{subfigure}
+  \caption{(a) Although the growth rate of total surrogate reactions decreases 
+  with time, it is likely that the curves will not fully plateau on a time scale
+  that we can reasonably simulate. (b) The growth rate appears to enter at least
+  three distinct regimes shown approximately by the different colored regions. We
+  fit Equation~\ref{eqn:plateau} to the last (green) regime. 
+  %(c) A power law 
+  %growth rate ($x^{-a}$) gives a superior fit to our simulation data compared to
+  %an exponential growth rate ($e^{-ax}$).
+  }\label{fig:plateau}
+  \end{figure}
+
+  We used bootstrapping to determine the mean value of $M$ with its associated
+  uncertainty. The procedure is as follows:
+  \begin{enumerate}
+  	\item Randomly choose, with replacement, 4 of the curves in Figure~\ref{fig:reacted_all}.
+  	\item Fit Equation~\ref{eqn:plateau} to the mean of the 4 curves to get the value of $M$.
+  	\item Repeat 200 times to generate a distribution of $M$ values. 
+  	\item Report mean and standard error of $M$ distribution.
+  \end{enumerate}
+  Note that this procedure is best performed with many more than 4 curves, however
+  it should still yield a more realistic uncertainty than the typically very small
+  error returned by the single non-linear least squares fit to the average.
+
   \pagebreak

### 2019-10-21 Ben_Manuscripts/stochastic_transport/Draft.tex
Updates to intro + methods, incorporating methanol and acetic acid

@@
 
-\title{Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II}
- Phase Lyotropic Liquid Crystal Membrane}
+\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
+and Predicts Long Timescale Behavior in Nanoscale Pores.}
 %MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
@@
 
+  %BJC4: Added next two paragraphs to help ease more into time series modeling
+  So far, our molecular models have provided valuable qualitative mechanistic insight 
+  with some quantitative support which already allows us to speculate about new LLC
+  monomer designs, however they would be of greater value to a wider audience if we 
+  could provide quantitative predictions of macroscopic observables such as solute 
+  flux. Due to the size of the system we are studying ($\sim$62,000 atoms) it is 
+  prohibitively expensive and time-consuming to run simulations longer than 
+  those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
+  size of our system, we only simulate 24 solute trajectories per unit cell in order
+  to minimize solute-solute interactions. This results in relatively high uncertainties
+  in observables such as mean squared displacement (MSD), preventing reliable long
+  timescale predictions. We are in need of a way of studying the collective motion
+  of a much larger set of solute over much longer timescales.
+
+  By reducing our MD simulations to observations of several key properties that 
+  have the greatest influence on solute dynamics, we can construct many realizations
+  of single solute trajectories useful for making long timescale predictions with 
+  computational ease and lower uncertainties. Fortunately, there is an abundance of 
+  information encoded in the complex solute trajectories. Into our model, we can 
+  incorporate fluctuations and time-dependent correlations in solute position as well
+  as the length of time solutes are trapped. We can add further detail by integrating
+  our time series analysis with our knowledge of the primary trapping mechanisms as
+  well as the solute's changing chemical environment within the heterogeneous membrane.
+
   In this work, we use the output of our MD simulations to construct two new classes of 
@@
   (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
-  The theory is frequently used to describe single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
+  These types of motion are frequently used alone or in combination to describe
+  single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
   %BJC4: consider rewording sentence below
   A CTRW is characterized by a distribution of hop lengths and dwell times, 
-  where trajectories are characterized by independent random draws from 
+  where trajectories are characterized by sequential independent random draws from 
   each distribution.\cite{montroll_random_1965} FBM is common in crowded,
@@
   and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
-  These processes can occur alone or in combination.
-
-  %BJC4: should I mention which anomalous subdiffusion model we chose? 
+
+  %BJC4: added mention of the anomalous subdiffusion model we chose 
   Our first modeling approach is based on the anomalous diffusion literature, 
   applying the mathematical formalism describing subdiffusive transport to observed
-  solute trajectories. We fit anomalous diffusion models in two ways: 
+  solute trajectories. Specifically, we treated our system as an FBM process subordinate
+  to a CTRW, or subordinated FBM (sFBM) for short. We fit sFBM
+  models in two ways: 
   %MRS4: can you clarify the sentence below? Probably something like: uses a single set of parameters in the diffusion equations, etc.
@@
   First, we parameterized solute motion using a single set of parameters fit
-  to a hypothesized anomalous diffusion model. Second, we use a two-state approach
-  extracting two sets of model parameters calculated based on a solute's radial
-  distance from the closest pore center.
-
-  %BJC4: might want to change the theme of this paragraph to something like: 
-  % Anomalous diffusion can help uncover mechanisms. Once we know mechanisms, we 
-  % can define them as states and use the MSDDM.
-  While elegant, pure anomalous diffusion theory may in some cases give only a 
-  qualitative understanding of transport mechanisms. 
-  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
-  %Relating it to molecular scale behavior and examples might help.
-  %BJC4: mention ageing
-  %BJC4: ?
-  Complex temporal relationships in 
-  between hops may have a significant effect on the average MSD. Inhomogeneity of 
-  a medium or multiple types of interactions may lead to a number of distinct 
-  diffusive regimes. In this case, a state based model may be useful.
+  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
+  by extracting two sets of model parameters calculated based on a solute's radial
+  distance from the closest pore center. We observe different dynamical behavior of
+  solute within the pore region versus within the monomer tails.
+
+  Where applicable, the sFBM model is an elegant way to characterize single 
+  particle trajectories and in addition to providing an easy and efficient way to 
+  simulate solute trajectories, can be helpful in uncovering the underlying 
+  solute-membrane interactions which result in observed transport mechanisms.
+  It can help researchers formulate hypotheses to explain why a certain set of
+  parameters is characteristic to a specific solute. This is largely the approach
+  we used to discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
+  Once one has knowledge of the primary mechanisms leading to anomalous diffusion
+  behavior, one may gain additional insight by formulating a state-based model.
+
+  %BJC4: Replaced below paragraph with above. 
+%  While elegant, pure anomalous diffusion theory may in some cases give only a 
+%  qualitative understanding of transport mechanisms. 
+%  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
+%  %Relating it to molecular scale behavior and examples might help.
+%  %BJC4: mention ageing
+%  %BJC4: ?
+%  Complex temporal relationships in 
+%  between hops may have a significant effect on the average MSD. Inhomogeneity of 
+%  a medium or multiple types of interactions may lead to a number of distinct 
+%  diffusive regimes. In this case, a state based model may be useful.
 
@@
   behavior in a coherent way. A model that successfully reproduces MD MSDs, but 
-  with nonsensical parameters has severely diminished value.
+  with nonsensical parameters has severely diminished value as it could be a 
+  consequence of luck.
 
@@
 
-  %BJC4: missing something about predictive capabilities
-
   We evaluate the two modeling approaches by using them to characterize the dynamical
@@
   three trapping mechanisms to different extents.
+
+  %BJC4: new
+  We find that the sFBM anomalous diffusion model does the best job of reproducing
+  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
+  how one could predict solute flux through a theoretical pore of with an 
+  experimentally relevant length.
 
@@
   % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
-  % BJC4: I think it'll be less confusing to me writing it to change it to z. Is it worth
-  % explicitly stating that z is the positional coordinate.
+  % BJC4: I think it'll be less confusing to me writing it to change it to z.
   Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
@@
   where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
-  diffusion coefficient. A value of $\alpha_d < 1$ indicates a subdiffusive process, 
-  while values of $\alpha_d = 1$ and $\alpha_d > 0$ are characteristic of Brownian and
-  superdiffusive motion respectively.
+  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
+  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
+  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 0$ 
+  are characteristic of Brownian and superdiffusive motion respectively.
 
@@
   calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
-  because we it is a more statistically robust measure of the average distance a solute
-  travels over time versus the ensemble average. Although theoretically possible, we do
+  because, compared to the ensemble average, it is a more statistically robust measure
+  of the average distance a solute travels over time. Although theoretically possible, we do
   not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
@@
 %  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
-  Because we are limited to taking measurements at discrete values dictated by the output 
+  Because we are limited to taking measurements at discrete intervals dictated by the output 
   frequency of our simulation trajectories, we fit the empirical dwell times
@@
   % because I haven't seen anyone do it this way.
-  sFBM implies correlated hops which we describe using the Hurst parameter, $H$. 
+  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
   The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
@@
   %MRS4: some justification on why 0.75 vs. any other cutoff.
-  %BJC4: I justified sentence after next. Is there something more I should say? 
+  %BJC4: I justified sentence after next. 
   as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
@@
   %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
+  %BJC4: made table
   \begin{table}[!htb]
@@
   % BJC3: will need to modify this text to reflect different lengths of simulations
-  For each solute, we simulated 10000 anomalous diffusion trajectories of length
+  For each solute, we simulated 10,000 anomalous diffusion trajectories of length
   $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
@@
   We reported the time-averaged MSD after time lags 40\% the length of the trajectory
-  with corresponding 95\% intervals.
-  %BJC3: Not sure if 40 % above is too long. I could do 20
-  %MRS4: is there some rule of thumb that could be used to justify the choice?
+  with corresponding 95\% confidence intervals.
   When simulating 2 mode models, we determined the state sequence based on random 
   draws weighted by the appropriate row of the probability transition matrix. We 
+  drew hops and dwells based on the current state of the system. Since we calculated
+  the transition probabilities from a finite data set, they have an associated 
+  uncertainty which we 
   %MRS4: not quite sure what you mean by incorporating uncertainty. 
-  %BJC4: The Dirichlet distribution basically perturbs the transition probabilities
-  % by an amount proportional to the number of observations. So things that don't
-  % get transition to/from frequently will have higher uncertainty. Output of 
-  % draw form Dirichlet distribution sums to 1. It doesn't really change the results
-  % much but I think it's good practice. In the 2D case, it is just a beta distribution
-  incorporated uncertainty into transition probabilities by drawing samples from a 
-  two dimensional Dirichlet distribution (also called a beta distribution) with concentration parameters defined by 
-  the count matrix.~\cite{bacallado_bayesian_2009} We drew hops and dwells based on
-  the current state of the system.
+  %BJC4: Added comment about having a finite amount of data with which to create transition matrix. Therefore it is uncertain
+  incorporated by re-sampling each row from a two dimensional Dirichlet distribution
+  (also called a beta distribution for the 2D case) with concentration parameters 
+  defined by the count matrix.~\cite{bacallado_bayesian_2009}
 
@@
   own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
-  ~\cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
+  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
   simulation algorithms for generating FLM trajectories, however, the algorithm
@@
 
-  When simulating MD-length FLM trajectories, we limited the maximum hop length based on where
-  the empirical hop distribution began to significantly under-sample the theoretical
-  maximum likelihood estimate (MLE) L\'evy stable distribution (see 
-  Section~\ref{S-section:truncation} of the Supporting Information).
-
-  % TODO?: This vvvv
-  For our 1 second simulations, we limited the maximum hop length to that seen by
-  the same solute undergoing Brownian motion in an unconfined aqueous environment. 
-  We have no reason to believe there is any kind of facilitated diffusion, so 
-  excursions characteristic of Brownian motion represent a reasonable upper limit
-  on hop lengths. To determine these limits we placed 24 solutes in a cubic box of 
-  water, 4 nm on each side. We allowed the solutes to diffuse for 100 ns, more than
-  ensuring the mean squared displacement entered a linear regime. We recorded the largest
-  observed hop length over a 0.5 ns time lag.
+%  BJC4: I already said this above
+%  When simulating MD-length FLM trajectories, we limited the maximum hop length based on where
+%  the empirical hop distribution began to significantly under-sample the theoretical
+%  maximum likelihood estimate (MLE) L\'evy stable distribution (see 
+%  Section~\ref{S-section:truncation} of the Supporting Information).
+
+%  For our 1 second simulations, we limited the maximum hop length to that seen by
+%  the same solute undergoing Brownian motion in an unconfined aqueous environment. 
+%  We have no reason to believe there is any kind of facilitated diffusion, so 
+%  excursions characteristic of Brownian motion represent a reasonable upper limit
+%  on hop lengths. To determine these limits we placed 24 solutes in a cubic box of 
+%  water, 4 nm on each side. We allowed the solutes to diffuse for 100 ns, more than
+%  ensuring the mean squared displacement entered a linear regime. We recorded the largest
+%  observed hop length over a 0.5 ns time lag.
 
@@
   pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
-  dimensional reduction.
+  dimensional reduction which are often necessary to identify representative states.
 
@@
   %BJC4: Tried to clarify in thesis statement. Let me know if you think it needs more
-  We verified the Markovianity of state transitions observed in our simulations 
+  We verified the Markovianity of state transitions by solutes in our MD simulations 
   by analyzing the empirically measured transition matrix. An important condition
@@
 
-  Adding to the standard MSM framework, we incorporate the dynamics of the solutes
-  within each state as well as the dynamics of state transitions, which include the
+  Adding to the standard MSM framework, we incorporated the dynamics of the solutes
+  within each state as well as the dynamics of state transitions, which includes the
   overall configurational state of the solute and it's environments. 
@@
   %BJC4: confusion here
-  state-dependent dynamics will allow us to
-  more accurately simulate solute trajectories. Hence we distinguish our model from 
-  MSMs by referring them as Markov State-Dependent Dynamical Models (MSDDMs).
+  state-dependent dynamics allows us to more accurately simulate solute trajectories.
+  %BJC4: I said below already
+  Hence we distinguish our model from MSMs by referring them as Markov State-Dependent
+  Dynamical Models (MSDDMs).
 
@@
   drawing subsequent states weighted by the rows of the probability transition matrix
-  corresponding to the particle's current state. 
-  %MRS4: not quite clear what you mean here by ``incorporated uncertainty''.  Any sort 
-  % of draws would result in different stochastic processes, which included uncertainty . . . 
-  Again we incorporated uncertainty into
-  the rows of the transition matrix by resampling them from a Dirichlet distribution. 
-  For each same-state subsequence of the full state sequence, we simulated an FLM process
-  using the Hurst parameter of that state and the parameters of the corresponding emission
-  distribution. Independently, we simulated the transition between each same-state 
-  sequence with an FLM process based on the Hurst parameter of transition sequences and 
-  the parameters of the single transition emission distribution. We used the same FLM 
-  simulation procedure described in Section~\ref{method:model_sFBM}.
+  corresponding to the particle's current state. Again, because we are working with a
+  finite data set, we incorporated uncertainty into the rows of the transition matrix 
+  by resampling them from a Dirichlet distribution. For each same-state subsequence of
+  the full state sequence, we simulated an FLM process using the Hurst parameter of that
+  state and the parameters of the corresponding emission distribution. Independently, 
+  we simulated the transition between each same-state sequence with an FLM process 
+  based on the Hurst parameter of transition sequences and the parameters of the 
+  single transition emission distribution. We used the same FLM simulation procedure
+  described in Section~\ref{method:model_sFBM}.
 
@@
 %  simulation procedure described in Section~\ref{method:model_sFBM}.
+
+  \subsection{Solute Flux}
 
@@
 
-  The model parameters are tabulated in Tables~\ref{table:sfbm_params} 
-  and~\ref{table:sfbm_params_2mode} and tell their own story about each solute's behavior. Using the 
-  techniques from Section~\ref{method:model_sFBM}, we extracted parameter values for each
-  solute in order to create 1 and 2 mode models, displayed in Tables~\ref{table:sfbm_params} 
-  and~\ref{table:sfbm_params_2mode} respectively. Higher values of $\sigma$ and lower
+  The model parameters for the 1 and 2 mode models are tabulated in 
+  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} respectively 
+  and tell their own story about each solute's behavior. 
+%  Using the techniques 
+%  from Section~\ref{method:model_sFBM}, we extracted parameter values for each
+%  solute in order to create 1 and 2 mode models, displayed in Tables~\ref{table:sfbm_params} 
+%  and~\ref{table:sfbm_params_2mode} respectively. 
+  Higher values of $\sigma$ and lower
   values of $\alpha_h$ indicate larger average hop length magnitudes by increasing the
@@
 
-  The parameters of the 1 mode model are similar between urea and ethylene glycol which 
-  is not surprising considering their similar MD MSDs. Dwell times by 
-  ethylene glycol are shorter as shown by its larger $\alpha_d$ and $\lambda$ values. Both
-  solutes make similarly sized hops with hop distributions that are relatively close 
-  to Gaussian (i.e. $\alpha_h$ near 2) when fit to a L\'evy stable distribution. Finally,
-  both solutes exhibit a similar degree of correlation between hops with ethylene glycol
-  exhibiting motion closer to Brownian.
-
-  The parameters of the 2 mode model are again similar between urea and ethylene glycol, 
-  but the difference between parameters of each mode offer more detailed mechanistic
-  insight than the 1 mode model. It is clear that solutes are significantly slowed while
-  they are in the tail region where long dwell times are more probable and hops are 
-  smaller. Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
-  heavy tailed relative to ethylene glycol which has an $\alpha_d$ more consistent 
-  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
-  the tails, it still has an appreciable probability of making large hops. This could 
-  be a consequence of urea's relatively small size and rigid shape compared to ethylene glycol.
+  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
+  of $\alpha_d$ for pure and truncated power law fits to the dwell time distributions of 
+  urea, ethylene glycol and methanol are similar. The value of $\alpha_d$ for acetic
+  acid is significantly lower than the rest of the solutes meaning it stays trapped 
+  for long periods of time more frequently. The value of $\lambda$ is largest for
+  methanol indicating that its longest dwell time is shorter than the longest dwell
+  times of all other solutes. When hops are fit to a Gaussian, it is clear that acetic
+  acid takes the smallest hops while methanol takes the largest. If we fit hops to a
+  L\'{e}vy stable distribution, we observe a similar trend in $\sigma$ values, but 
+  with varying weights on the distribution's tails. Acetic acid has the heaviest
+  tails (lowest $\alpha_h$), meaning it is more likely to take large hops, while 
+  ethylene glycol stays close to a Gaussian distribution (i.e. $\alpha_h$ near 2).
+  The Hurst parameters indicate a moderate degree of anti-correlation between hops. 
+  Surprisingly, methanol takes the most anti-correlated hops (lowest $H$). This is
+  likely because methanol spends the largest fraction of its time within the pores. 
+  It can still make large hops thanks to its small size, but tends to bounce around
+  the tails.
+
+%  BJC4: urea and ethylene glycol only
+%  The parameters of the 1 mode model are similar between urea and ethylene glycol which 
+%  is not surprising considering their similar MD MSDs. Dwell times by 
+%  ethylene glycol are shorter as shown by its larger $\alpha_d$ and $\lambda$ values. Both
+%  solutes make similarly sized hops with hop distributions that are relatively close 
+%  to Gaussian (i.e. $\alpha_h$ near 2) when fit to a L\'evy stable distribution. Finally,
+%  both solutes exhibit a similar degree of correlation between hops with ethylene glycol
+%  exhibiting motion closer to Brownian.
+
+  The difference in parameters of each mode of the 2 mode sFBM model offer additional
+  mechanistic insight which the 1 mode model lacks. It is clear that solutes are 
+  significantly slowed while they are in the tail region (mode 2) where long dwell times
+  are more probable and hops are smaller (smaller $\alpha_d$). 
+% BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
+% The values of $\lambda$, however, do not 
+% appear to be directly correlated to mode. For example, $\lambda$ for ethylene glycol is
+% lower in the pores, meaning its longest dwell times in the pores are longer than its
+% longest dwell times in the tails. This may be a consequence of    
+  Interestingly, $\alpha_h$ for urea and acetic acid in mode 2 is 1.50 meaning its 
+  hop distribution is heavy tailed relative to ethylene glycol and methanol whose 
+  $\alpha_h$ values are more consistent with a Gaussian distribution. Acetic acid and
+  urea are structurally similar molecules, both planar with two heavy atoms attached to
+  a carbonyl group. Their small size and rigid shape may allow them to slip through 
+  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
+  larger jumps to escape traps.
+
+%  BJC4: Urea and ethlyene glycol only
+%  The parameters of the 2 mode model are again similar between urea and ethylene glycol, 
+%  but the difference between parameters of each mode offer more detailed mechanistic
+%  insight than the 1 mode model. It is clear that solutes are significantly slowed while
+%  they are in the tail region where long dwell times are more probable (lower $\alpha_d$)
+%  and hops are smaller (smaller $\sigma$).  
+%  Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
+%  heavy tailed relative to ethylene glycol which has an $\alpha_d$ more consistent 
+%  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
+%  the tails, it still has an appreciable probability of making large hops. This could 
+%  be a consequence of urea's relatively small size and rigid shape compared to ethylene glycol.
   %Ethylene glycol is a linear chain that can
@@
   \centering
-  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|}
+  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
   \hline
-  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol \\
-  \hline
-  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            \\\cline{2-4}
-  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    \\\hline
-  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            \\\cline{2-4}
-  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      \\\hline
-  Correlation   & $\gamma(H)$               & 0.37         & 0.40            \\
+  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
+  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
+  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
+  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
+  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
+  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
   \hline 
@@
   \centering
-  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
+  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
   \hline
-  \multicolumn{5}{|c|}{2 Mode Model} \\\hline
-                & Parameters                               & Mode & Urea         & Ethylene Glycol \\
+  \multicolumn{7}{|c|}{2 Mode Model} \\\hline
+                & Parameters                               & Mode & Urea         & Ethylene Glycol &  Methanol    & Acetic Acid \\
   \hline
-                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           \\\cline{3-5}
-  Dwell         &                                          & 2    & 0.38         &  0.48           \\\cline{2-5}
-  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   \\\cline{3-5}
-                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   \\\hline
-                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           \\\cline{3-5}
-  Hop           &                                          & 2    & 0.24         &  0.23           \\\cline{2-5}
-  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     \\\cline{3-5}
-                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     \\\hline
-  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           \\\cline{3-5}
+                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.92         & 0.58         \\\cline{3-7}
+  Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
+  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.07, 0.0005 & 0.41, 0.0026 \\\cline{3-7}
+                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.32, 0.0049 & 0.00, 0.0021 \\\hline
+                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.43         & 0.32         \\\cline{3-7}
+  Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
+  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.28, 1.87   & 0.21, 1.91   \\\cline{3-7}
+                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.80   & 0.09, 1.50   \\\hline
+  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
   \hline 
@@
 
-  Our models reasonably predict the MD simulated MSDs. Using the parameters in 
+  Our models can reasonably predict the MD simulated MSDs. Using the parameters in 
   Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} as inputs, we compared
@@
   \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{1mode_msd_comparison_MET.pdf}
-%  \caption{Methanol}\label{fig:1mode_msd_comparison_MET}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH.pdf}
-%  \caption{Acetic Acid}\label{fig:1mode_msd_comparison_ACH}
-%  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_MET.pdf}
+  \caption{Methanol}\label{fig:1mode_msd_comparison_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:1mode_msd_comparison_ACH}
+  \end{subfigure}
   \caption{MSDs generated from realizations of our 1 mode anomalous diffusion models
@@
   \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{2mode_msd_comparison_MET.pdf}
-%  \caption{Methanol}\label{fig:2mode_msd_comparison_MET}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH.pdf}
-%  \caption{Acetic Acid}\label{fig:2mode_msd_comparison_ACH}
-%  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_MET.pdf}
+  \caption{Methanol}\label{fig:2mode_msd_comparison_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:2mode_msd_comparison_ACH}
+  \end{subfigure}
   \caption{MSDs generated from realization of our 2-mode anomalous diffusion model
@@
 
+  We further validated our models by training the parameters on half of the 
+  equilibrated trajectories and then using them to predict the MSD calculated
+  from the alternate half of the trajectories. We trained on both the first
+  and second half of the data. At equilibrium, the parameter estimates should 
+  be the same, within error, for either portion of the data used for training.
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{|M{1.75cm}|M{1.65cm}|M{2cm}|M{2cm}|M{2cm}|M{2cm}|}
+  \hline
+  \multirow{2}{*}{Solute}&\multirow{2}{*}{Model}& \multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{3-6}
+                              &        & MSD                     & Prediction & MSD                 & Prediction \\\hline
+  \multirow{2}{*}{Urea}       & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
+                              & sFLMcut&                         &            &                     &            \\\hline
+  Ethylene                    & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
+  Glycol                      & sFLMcut&                         &            &                     &            \\\hline
+  \multirow{2}{*}{Methanol}   & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
+                              & sFLMcut&                         &            &                     &            \\\hline
+  \multirow{2}{*}{Acetic Acid}& sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
+                              & sFLMcut&                         &            &                     &            \\\hline
+  \end{tabular}
+  \caption{}\label{table:sFBM_train}
+  \end{table}
+
   %BJC3: Is it a bad idea to acknowledge that there is no experimental data? I can 
@@
 
+  % BJC4: Say something about pore entry and exit as an improvement to the model
+
   We have tested two different mathematical frameworks for describing solute

### 2019-10-21 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Updates to intro + methods, incorporating methanol and acetic acid

@@
   \newcolumntype{A}{ >{\centering\arraybackslash} m{2.5in} }
-  \newcolumntype{B}{ >{\centering\arraybackslash} m{0.75in} }
-  \newcolumntype{C}{m{2.75in}}
+  \newcolumntype{B}{ >{\centering\arraybackslash} m{0.5in} }
+  \newcolumntype{C}{m{3in}}
   \begin{tabular}{|A|B|C|}
@@
   % mimic this
-  \texttt{/setup/param.sh} & 2.1 & Parameterize liquid
-  crystal monomers and solutes with GAFF \\ \hline
+  \texttt{/setup/parameterize.py}            & 2.1 & Parameterize liquid crystal monomers and solutes with GAFF \\ \hline
+  \texttt{/setup/build.py}                   & 2.1 & Build simulation unit cell \\ \hline
+  \texttt{/setup/place\_solutes\_pores.py}   & 2.1 & Place equispaced solutes in the pore centers of a unit cell \\\hline
+  \texttt{/setup/equil.py}                   & 2.1 & Equilibrate unit cell and run production simulation \\\hline
+  \texttt{/analysis/solute\_partitioning.py} & 2.1 & Determine time evolution of partition of solutes between pores and tails \\\hline
+  \texttt{/timeseries/msd.py}                & 2.2 & Calculate the mean squared displacement of solutes \\\hline
+  \texttt{/analysis/sfbm\_parameters.py}     & 2.2 & Get subordinated fractional Brownian motion parameters by fitting to a solute's dwell and hop length distributions and positional autocorrelation function.
+\\\hline
+  \texttt{/timeseries/ctrwsim.py}            & 2.2 & Generate realizations of a continuous time random walk with the user's choice of dwell and hop distributions \\\hline
+  \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
+  \texttt{/analysis/ markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
 

### 2019-10-21 LLC_Membranes/timeseries/forecast_ctrw.py

@@ -122,10 +122,10 @@ if __name__ == "__main__":
 
         sys.hops_and_dwells(penalty=fit['breakpoint_penalty'])
 
-        sys.fit_distributions(nbins=fit['bins'], nboot=fit['nboot'], plot=True, show=False, save=True,
+        sys.fit_distributions(nbins=fit['bins'], nboot=fit['nboot'], plot=False, show=False, save=True,
                               dwell_distribution=fit['dwell_distribution'], hop_distribution=fit['hop_distribution'])
 
-        sys.estimate_hurst(modes=fit['hurst_modes'])
+        sys.estimate_hurst(modes=fit['hurst_modes'], show=False)
 
         if args.update:
             sys.update_database()

### 2019-10-22 Ben_Manuscripts/stochastic_transport/Draft.tex
Anomalous diffusion analysis

@@
   However, since there are no known exact simulation techniques for generating 
-  realizations of fractional L\'evy motion, we must explore whether this more general
+  realizations of fractional L\'evy motion, we must evaluate whether this more general
   fit is worthwhile.
@@
   power law behavior since it is consistent with most theoretical descriptions of CTRWs.
-  The data fits well to this model at short dwell times but
-  the density of long dwell times is over-estimated. In our second approach, we truncate
-  the power law distribution with an exponential cut-off, lowering the probability of
-  long dwell times. We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where the
+  The data fits well to this model at short dwell times but the density of long dwell
+  times is over-estimated. In our second approach, we truncate the power law distribution
+  with an exponential cut-off, lowering the probability of extremely long dwell times. 
+  We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where the
   density of the truncated power law drops below that of the pure power law and tends towards
   0 near a dwell time of 250 ns.
-
-  The model parameters for the 1 and 2 mode models are tabulated in 
-  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} respectively 
-  and tell their own story about each solute's behavior. 
-%  Using the techniques 
-%  from Section~\ref{method:model_sFBM}, we extracted parameter values for each
-%  solute in order to create 1 and 2 mode models, displayed in Tables~\ref{table:sfbm_params} 
-%  and~\ref{table:sfbm_params_2mode} respectively. 
-  Higher values of $\sigma$ and lower
-  values of $\alpha_h$ indicate larger average hop length magnitudes by increasing the
-  hop length distribution's width and tail density respectively. Higher values of $\alpha_d$
-  indicate a lower probability of long dwell times. Higher values of $\lambda$ truncate
-  the power law distribution earlier preventing extremely long dwell times. Values of $H$
-  closer to the Brownian limit of 0.5, indicate a lower degree of negative correlation 
-  between hops. All of which contribute to an overall increase in the MSD.
-
-  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
-  of $\alpha_d$ for pure and truncated power law fits to the dwell time distributions of 
-  urea, ethylene glycol and methanol are similar. The value of $\alpha_d$ for acetic
-  acid is significantly lower than the rest of the solutes meaning it stays trapped 
-  for long periods of time more frequently. The value of $\lambda$ is largest for
-  methanol indicating that its longest dwell time is shorter than the longest dwell
-  times of all other solutes. When hops are fit to a Gaussian, it is clear that acetic
-  acid takes the smallest hops while methanol takes the largest. If we fit hops to a
-  L\'{e}vy stable distribution, we observe a similar trend in $\sigma$ values, but 
-  with varying weights on the distribution's tails. Acetic acid has the heaviest
-  tails (lowest $\alpha_h$), meaning it is more likely to take large hops, while 
-  ethylene glycol stays close to a Gaussian distribution (i.e. $\alpha_h$ near 2).
-  The Hurst parameters indicate a moderate degree of anti-correlation between hops. 
-  Surprisingly, methanol takes the most anti-correlated hops (lowest $H$). This is
-  likely because methanol spends the largest fraction of its time within the pores. 
-  It can still make large hops thanks to its small size, but tends to bounce around
-  the tails.
-
-%  BJC4: urea and ethylene glycol only
-%  The parameters of the 1 mode model are similar between urea and ethylene glycol which 
-%  is not surprising considering their similar MD MSDs. Dwell times by 
-%  ethylene glycol are shorter as shown by its larger $\alpha_d$ and $\lambda$ values. Both
-%  solutes make similarly sized hops with hop distributions that are relatively close 
-%  to Gaussian (i.e. $\alpha_h$ near 2) when fit to a L\'evy stable distribution. Finally,
-%  both solutes exhibit a similar degree of correlation between hops with ethylene glycol
-%  exhibiting motion closer to Brownian.
-
-  The difference in parameters of each mode of the 2 mode sFBM model offer additional
-  mechanistic insight which the 1 mode model lacks. It is clear that solutes are 
-  significantly slowed while they are in the tail region (mode 2) where long dwell times
-  are more probable and hops are smaller (smaller $\alpha_d$). 
-% BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
-% The values of $\lambda$, however, do not 
-% appear to be directly correlated to mode. For example, $\lambda$ for ethylene glycol is
-% lower in the pores, meaning its longest dwell times in the pores are longer than its
-% longest dwell times in the tails. This may be a consequence of    
-  Interestingly, $\alpha_h$ for urea and acetic acid in mode 2 is 1.50 meaning its 
-  hop distribution is heavy tailed relative to ethylene glycol and methanol whose 
-  $\alpha_h$ values are more consistent with a Gaussian distribution. Acetic acid and
-  urea are structurally similar molecules, both planar with two heavy atoms attached to
-  a carbonyl group. Their small size and rigid shape may allow them to slip through 
-  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
-  larger jumps to escape traps.
-
-%  BJC4: Urea and ethlyene glycol only
-%  The parameters of the 2 mode model are again similar between urea and ethylene glycol, 
-%  but the difference between parameters of each mode offer more detailed mechanistic
-%  insight than the 1 mode model. It is clear that solutes are significantly slowed while
-%  they are in the tail region where long dwell times are more probable (lower $\alpha_d$)
-%  and hops are smaller (smaller $\sigma$).  
-%  Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
-%  heavy tailed relative to ethylene glycol which has an $\alpha_d$ more consistent 
-%  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
-%  the tails, it still has an appreciable probability of making large hops. This could 
-%  be a consequence of urea's relatively small size and rigid shape compared to ethylene glycol.
-  %Ethylene glycol is a linear chain that can
-  %easily become entangled among the alkane tails while urea is planar with its four
-  %heavy atoms bonded to a single central atom.
 
@@
   \hline
-                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.92         & 0.58         \\\cline{3-7}
+                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.90         & 0.58         \\\cline{3-7}
   Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
-  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.07, 0.0005 & 0.41, 0.0026 \\\cline{3-7}
-                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.32, 0.0049 & 0.00, 0.0021 \\\hline
-                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.43         & 0.32         \\\cline{3-7}
+  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.04, 0.0006 & 0.41, 0.0026 \\\cline{3-7}
+                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.30, 0.0054 & 0.00, 0.0021 \\\hline
+                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.45         & 0.32         \\\cline{3-7}
   Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
-  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.28, 1.87   & 0.21, 1.91   \\\cline{3-7}
-                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.80   & 0.09, 1.50   \\\hline
+  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.31, 1.97   & 0.21, 1.91   \\\cline{3-7}
+                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.85   & 0.09, 1.50   \\\hline
   Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
@@
   \end{tabular}
-  %MRS4: more about what the consequences of these results are?
-  \caption{To create a 2 mode model, we generated a set of parameters based on solute
-  behavior as function of distance from the pore center. Mode 1 corresponds to solute
-  behavior within 0.75 nm of the pore center and mode 2 corresponds to behavior greater
-  than or equal to 0.75 nm from the pore center. Note that we used the same Hurst parameter
-  for both modes due to a low number of sufficiently long sequences of hops in each mode. 
-  See Table~\ref{table:sfbm_params} for descriptions of the parameters.}\label{table:sfbm_params_2mode}
+  \caption{The two model parameterizes solute behavior in the pores and tails separately. 
+  Generally, movement is much more restricted in the tail region. To create a 2 mode model,
+  we generated a set of parameters based on solute behavior as function of distance from
+  the pore center. Mode 1 corresponds to solute behavior within 0.75 nm of the pore center
+  and mode 2 corresponds to behavior greater than or equal to 0.75 nm from the pore center.
+  Note that we used the same Hurst parameter for both modes due to a low number of 
+  sufficiently long sequences of hops in each mode. See Table~\ref{table:sfbm_params} for
+  descriptions of the parameters.}\label{table:sfbm_params_2mode}
   \end{table}
 
-  Our models can reasonably predict the MD simulated MSDs. Using the parameters in 
-  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} as inputs, we compared
-  the MSD of simulated anomalous diffusion trajectories to MD simulated MSDs. The MSD
-  curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs
-  for comparison in Figures~\ref{fig:anomalous_msds_1mode} and 
-  Figure~\ref{fig:anomalous_msds_2mode} respectively.
+  Using the parameters in Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}
+  as inputs to our models, we obtain reasonable predictions of the MD simulated MSDs. The 
+  MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
+  comparison in Figures~\ref{fig:anomalous_msds_1mode} and Figure~\ref{fig:anomalous_msds_2mode}
+  respectively. Our anomalous diffusion trajectories have a significantly reduced 
+  uncertainty and lie well within the error bars of MD.
 
@@
   Truncating the power laws with an exponential cut-off has the largest effect on the on 
-  the match between MD MSD and simulated anomalous diffusion trajectories. Without 
-  truncation, the MD MSDs are underestimated. This is because dwell times on the order 
-  of the MD simulation length are sampled and incorporated into the simulated anomalous
-  diffusion trajectories, reducing the MSD. The longest observed dwell time among the
-  solutes was 1.3 $\mu$s by ethylene glycol.
+  the match between the MD-calculated MSD and that measured from the simulated anomalous
+  diffusion trajectories. Without truncation, the MD MSDs are underestimated in all cases.
+  This is because dwell times on the order of the MD simulation length are sampled and 
+  incorporated into the simulated anomalous diffusion trajectories, reducing the MSD. 
+  The longest observed dwell time among the solutes was 1.3 $\mu$s by ethylene glycol.
 
@@
   glycol in the 2 mode model where the L\'evy index for both modes is near 2, indicating
-  a near Gaussian distribution, but the MLE of the $\sigma$ values of the L\'evy stable
-  distribution are much smaller than the Gaussian MLE $\sigma$ values.
-  %BJC3: I need to investigate this. How could sigma be so far underestimated if basically Gaussian
-
-  % BJC3: I'd like to present the parameter values because they give clues
-  % towards mechanisms
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{|c|c|c|c|c|}
-%  \hline
-%  \multirow{4}{*}{Model} & \multicolumn{4}{c|}{Urea} \\\cline{2-5}
-%  & \multicolumn{4}{c|}{Single Mode (H = 0.37)} \\\cline{2-5}
-%  & \multicolumn{2}{c|}{Dwells} & \multicolumn{2}{c|}{hops} \\\cline{2-5}
-%  & $\alpha$ & $\lambda$ & $\sigma$ & $\alpha$ \\\hline
-%  sFBM   & 0.57 & --     & 0.33 & --   \\
-%  sFBMcut& 0.40 & 0.0024 & 0.33 & --   \\
-%  sFLM   & 0.57 & --     & 0.21 & 1.84 \\
-%  sFLMcut& 0.40 & 0.0024 & 0.21 & 1.84 \\
-%  \hline
-%  \end{tabular}
-%  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
-%  trajectories and then computed the average ensemble-averaged MSD of 10000 
-%  simulated trajectories.}\label{table:sfbm_params}
-%  \end{table}
-
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
-%  \hline
-%  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol & Methanol & Acetic Acid \\
-%  \hline
-%  Dwell         & $P(\alpha_d)$             & 0.57         & & & \\
-%  Distributions & $P_T(\alpha_d, \lambda)$  & (0.4, 0.0024)& & & \\
-%  \hline
-%  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & & & \\
-%  Distributions & $L(\sigma, \alpha_h)$     & (0.21, 1.84) & & & \\
-%  \hline
-%  Correlation   & $\gamma(H)$               & 0.37         & & & \\
-%  \hline 
-%  \end{tabular}
-%  \caption{To create a 1 mode model for each solute, we parameterized a pure power
-%  law ($P(\alpha_d)$) and a truncated power law $P_T(\alpha_d, \lambda)$ distribution 
-%  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
-%  law tails and higher values of $\lambda$ truncate the distribution at lower
-%  dwell times. We parameterized Gaussian ($\mathcal{N}$) and L\'evy stable 
-%  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
-%  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
-%  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
-%  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
-%  function ($\gamma(H)$) to describe the degree of correlation between hops. 
-%  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
-%  \end{table}
-%  
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
-%  \hline
-%  2 Mode Model  & Parameters                               & Mode & Urea         & Ethylene Glycol & Methanol & Acetic Acid \\
-%  \hline
-%                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.57         & & & \\\cline{3-7}
-%  Dwell         &                                          & 2    & 0.57         & & & \\\cline{2-7}
-%  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    &(0.4, 0.0024) & & & \\\cline{3-7}
-%                &                                          & 2    &(0.4, 0.0024) & & & \\\hline
-%                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.33         & & & \\\cline{3-7}
-%  Hop           &                                          & 2    & (0.21, 1.84) & & & \\\cline{2-7}
-%  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.33         & & & \\\cline{3-7}
-%                &                                          & 2    & (0.21, 1.84) & & & \\\hline
-%  \multirow{2}{*}{Correlation}&\multirow{2}{*}{$\gamma(H)$}& 1    & 0.37         & & & \\\cline{3-7}
-%                &                                          & 2    & 0.37         & & & \\\cline{3-7}
-%  \hline 
-%  \end{tabular}
-%  \caption{To create a 2 mode model, we generated a set of parameters based on solute
-%  behavior as function of distance from the pore center. Mode 1 corresponds to solute
-%  behavior within 0.75 nm of the pore center and mode 2 corresponds to behavior greater
-%  than or equal to 0.75 nm from the pore center. See Table~\ref{table:sfbm_params}
-%  for descriptions of the parameters.}\label{table:sfbm_params_2mode}
-%  \end{table}
+  a near Gaussian distribution.
+
+  The model parameters for the 1 and 2 mode models tell stories about each solute's behavior. 
+  Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
+  hop length magnitudes by increasing the hop length distribution's width and tail 
+  density respectively. Higher values of $\alpha_d$ indicate a lower probability of 
+  long dwell times. Higher values of $\lambda$ truncate the power law distribution 
+  earlier preventing extremely long dwell times. Values of $H$ closer to the Brownian
+  limit of 0.5, indicate a lower degree of negative correlation between hops. All 
+  of which contribute to an overall increase in the MSD.
+
+  Turning first to the parameters of the 1 mode model, we can begin to break down the
+  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
+  relatively similar which is consistent with their similar MD-measured MSDs. Methanol 
+  tends to stay trapped for less time and takes larger hops but the most substantial
+  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
+  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
+  it appears that our model consistently under-predicts the methanol MSD curve relative
+  to other solutes. However, it remains plausible that methanol does have a low $H$ 
+  value because it spends the majority of its time outside the pore region where collisions
+  with tails are frequent. Urea has the third highest MSD which is influenced primarily
+  by more frequent and long dwell times, indicated by lower values of $\alpha_d$ and 
+  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
+  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
+  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
+  by an $\alpha_d$ value significantly lower than other solutes, but an intermediate 
+  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
+  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
+  (lower $\alpha_h$) than the other solutes.
+
+  We can use the 2 mode model to gain an even deeper understanding of solute behavior
+  in the pore versus in the tails. It is clear that solutes are significantly slowed 
+  while they are in the tail region (mode 2) where long dwell times are more probable
+  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
+  $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
+  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
+  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
+  structurally similar molecules, both planar with two heavy atoms attached to a 
+  carbonyl group. Their small size and rigid shape may allow them to slip through 
+  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
+  larger jumps to escape traps.
+
+%  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
+%  of $\alpha_d$ for pure and truncated power law fits to the dwell time distributions of 
+%  urea, ethylene glycol and methanol are similar. The value of $\alpha_d$ for acetic
+%  acid is significantly lower than the rest of the solutes meaning it stays trapped 
+%  for long periods of time more frequently. The value of $\lambda$ is largest for
+%  methanol indicating that its longest dwell time is shorter than the longest dwell
+%  times of all other solutes. When hops are fit to a Gaussian, it is clear that acetic
+%  acid takes the smallest hops while methanol takes the largest. If we fit hops to a
+%  L\'{e}vy stable distribution, we observe a similar trend in $\sigma$ values, but 
+%  with varying weights on the distribution's tails. Acetic acid has the heaviest
+%  tails (lowest $\alpha_h$), meaning it is more likely to take large hops, while 
+%  ethylene glycol stays close to a Gaussian distribution (i.e. $\alpha_h$ near 2).
+%  The Hurst parameters indicate a moderate degree of anti-correlation between hops. 
+%  Surprisingly, methanol takes the most anti-correlated hops (lowest $H$). This is
+%  likely because methanol spends the largest fraction of its time within the pores. 
+%  It can still make large hops thanks to its small size, but tends to bounce around
+%  the tails.
+
+%  BJC4: urea and ethylene glycol only
+%  The parameters of the 1 mode model are similar between urea and ethylene glycol which 
+%  is not surprising considering their similar MD MSDs. Dwell times by 
+%  ethylene glycol are shorter as shown by its larger $\alpha_d$ and $\lambda$ values. Both
+%  solutes make similarly sized hops with hop distributions that are relatively close 
+%  to Gaussian (i.e. $\alpha_h$ near 2) when fit to a L\'evy stable distribution. Finally,
+%  both solutes exhibit a similar degree of correlation between hops with ethylene glycol
+%  exhibiting motion closer to Brownian.
+
+%  The difference in parameters of each mode of the 2 mode sFBM model offer additional
+%  mechanistic insight which the 1 mode model lacks. It is clear that solutes are 
+%  significantly slowed while they are in the tail region (mode 2) where long dwell times
+%  are more probable and hops are smaller (smaller $\alpha_d$). 
+% BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
+% The values of $\lambda$, however, do not 
+% appear to be directly correlated to mode. For example, $\lambda$ for ethylene glycol is
+% lower in the pores, meaning its longest dwell times in the pores are longer than its
+% longest dwell times in the tails. This may be a consequence of    
+%  Interestingly, $\alpha_h$ for urea and acetic acid in mode 2 is 1.50 meaning its 
+%  hop distribution is heavy tailed relative to ethylene glycol and methanol whose 
+%  $\alpha_h$ values are more consistent with a Gaussian distribution. Acetic acid and
+%  urea are structurally similar molecules, both planar with two heavy atoms attached to
+%  a carbonyl group. Their small size and rigid shape may allow them to slip through 
+%  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
+%  larger jumps to escape traps.
+
+%  BJC4: Urea and ethlyene glycol only
+%  The parameters of the 2 mode model are again similar between urea and ethylene glycol, 
+%  but the difference between parameters of each mode offer more detailed mechanistic
+%  insight than the 1 mode model. It is clear that solutes are significantly slowed while
+%  they are in the tail region where long dwell times are more probable (lower $\alpha_d$)
+%  and hops are smaller (smaller $\sigma$).  
+%  Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
+%  heavy tailed relative to ethylene glycol which has an $\alpha_d$ more consistent 
+%  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
+%  the tails, it still has an appreciable probability of making large hops. This could 
+%  be a consequence of urea's relatively small size and rigid shape compared to ethylene glycol.
+  %Ethylene glycol is a linear chain that can
+  %easily become entangled among the alkane tails while urea is planar with its four
+  %heavy atoms bonded to a single central atom.
 
@@
   \centering
-  \begin{tabular}{|M{1.75cm}|M{1.65cm}|M{2cm}|M{2cm}|M{2cm}|M{2cm}|}
+  \begin{tabular}{|M{1.75cm}|M{1cm}|M{1.65cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|}
   \hline
-  \multirow{2}{*}{Solute}&\multirow{2}{*}{Model}& \multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{3-6}
-                              &        & MSD                     & Prediction & MSD                 & Prediction \\\hline
-  \multirow{2}{*}{Urea}       & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
-                              & sFLMcut&                         &            &                     &            \\\hline
-  Ethylene                    & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
-  Glycol                      & sFLMcut&                         &            &                     &            \\\hline
-  \multirow{2}{*}{Methanol}   & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
-                              & sFLMcut&                         &            &                     &            \\\hline
-  \multirow{2}{*}{Acetic Acid}& sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
-                              & sFLMcut&                         &            &                     &            \\\hline
+  \multirow{2}{*}{Solute}&\multirow{2}{*}{Modes}&\multirow{2}{*}{Model}&\multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{4-7}
+                              &                   &        & MD MSD                & Prediction & MD MSD               & Prediction \\\hline
+  \multirow{4}{*}{Urea}       & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.43 (1.11, 1.76)}&0.31 (0.28, 0.35)&\multirow{4}{*}{1.43 (1.11, 1.77)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
+                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+                              &                   &sFLMcut&                         &            &                     &            \\\hline
+                              & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.03 (0.79, 1.29)}        &            &\multirow{4}{*}{1.03 (0.77, 1.30)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+  Ethylene                    &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
+  Glycol                      &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+                              &                   &sFLMcut&                         &            &                     &            \\\hline
+  \multirow{4}{*}{Methanol}   &\multirow{2}{*}{1} &sFBMcut&\multirow{4}{*}{1.06 (0.69, 1.36)}        &            &\multirow{4}{*}{1.06 (0.67, 1.37)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+                              &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
+                              &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+                              &                   &sFLMcut&                         &            &                     &            \\\hline
+  \multirow{4}{*}{Acetic Acid}& \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{0.35 (0.28, 0.45)}&0.31 (0.28, 0.35)&\multirow{4}{*}{0.35 (0.26, 0.47)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
+                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+                              &                   &sFLMcut&                         &            &                     &            \\\hline
   \end{tabular}
@@
 
-  To create an MSDDM for each solute, we generated emission distributions based 
-  on transitions from each state and transitions between states. There are not
+  %BJC4: maybe some kind of transitional paragraph here.
+
+  To create an MSDDM for each solute, we generated emission distributions for
+  fluctuations within each state and transitions between states. There are not
   enough consecutive observations of each type of transition with which to study
@@
   into a single distribution and measured the correlation of the series of all 
-  transitions. We lose information about individual types of transitions however, 
+  transitions. We lose information about individual types of transitions, however, 
   we believe this is unavoidable without at least an order of magnitude of additional data.
@@
   %MRS4: might this work better visually?  Table in SI, figure here?
-  %BJC4: like a bar plot?
+  %BJC4: Somehow I'd need to fit 108 pieces of data into a figure
   \begin{figure}
@@
 
-%  %BJC3: TODO automate this table
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-%  \hline
-%  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
-%  State & H     & $\alpha$ & $\sigma$ & H    & $\alpha$ & $\sigma$ & H & $\alpha$ & $\sigma$ & H & $\alpha$ & $\sigma$ \\\hline
-%  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045    &   &          &           &  &          &           \\
-%  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037    &   &          &           &  &          &           \\
-%  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030    &   &          &           &  &          &           \\
-%  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028    &   &          &           &  &          &           \\
-%  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062    &   &          &           &  &          &           \\
-%  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040    &   &          &           &  &          &           \\
-%  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040    &   &          &           &  &          &           \\
-%  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030    &   &          &           &  &          &           \\
-%  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045    &   &          &           &  &          &           \\\hline
-%  \end{tabular}
-%  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
-%  trajectories and then computed the average ensemble-averaged MSD of 10000 
-%  simulated trajectories.}\label{table:msddm_params}
-%  \end{table}
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+  \hline
+  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
+  State & H     & $\alpha$ & $\sigma$ & H    & $\alpha$ & $\sigma$   & H     & $\alpha$ & $\sigma$ & H    & $\alpha$ & $\sigma$ \\\hline
+  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045      & 0.11  & 1.56     & 0.052    & 0.10 & 1.78     & 0.035    \\
+  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037      & 0.07  & 1.63     & 0.043    & 0.08 & 1.88     & 0.032    \\
+  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030      & 0.02  & 1.80     & 0.036    & 0.04 & 2.00     & 0.030    \\
+  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028      & 0.02  & 1.75     & 0.036    & 0.04 & 2.00     & 0.027    \\
+  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062      & 0.10  & 1.28     & 0.074    & 0.13 & 1.47     & 0.048    \\
+  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040      & 0.03  & 1.50     & 0.042    & 0.09 & 1.70     & 0.038    \\
+  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040      & 0.28  & 1.20     & 0.043    & 0.08 & 1.77     & 0.031    \\
+  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030      & 0.04  & 1.83     & 0.037    & 0.01 & 2.00     & 0.030    \\
+  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045      & 0.35  & 1.45     & 0.057    & 0.34 & 1.54     & 0.040    \\\hline
+  \end{tabular}
+  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
+  trajectories and then computed the average ensemble-averaged MSD of 1000 
+  simulated trajectories. The states are defined in Table~\ref{table:states}
+  except state T which refers to the transition emissions.}\label{table:msddm_params}
+  \end{table}
 %  
@@
 
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
-  \hline
-  & \multicolumn{3}{c|}{Urea}                      & \multicolumn{3}{c|}{Ethylene Glycol} \\\hline
-  State & H     & $\alpha_h$ & $\sigma$  & H    & $\alpha_h$ & $\sigma$ \\\hline
-  1     & 0.10  & 1.79       & 0.034     & 0.09 & 1.68       & 0.045    \\
-  2     & 0.06  & 1.80       & 0.033     & 0.09 & 1.75       & 0.037    \\
-  3     & 0.11  & 1.88       & 0.030     & 0.11 & 1.86       & 0.030    \\
-  4     & 0.10  & 1.95       & 0.027     & 0.04 & 1.91       & 0.028    \\
-  5     & 0.19  & 1.34       & 0.048     & 0.15 & 1.40       & 0.062    \\
-  6     & 0.15  & 1.45       & 0.040     & 0.11 & 1.52       & 0.040    \\
-  7     & 0.15  & 1.61       & 0.032     & 0.05 & 1.60       & 0.040    \\
-  8     & 0.11  & 1.71       & 0.028     & 0.05 & 1.74       & 0.030    \\
-  T     & 0.34  & 1.42       & 0.036     & 0.37 & 1.44       & 0.045    \\\hline
-  \end{tabular}
-  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
-  trajectories and then computed the average ensemble-averaged MSD of 10000 
-  simulated trajectories. The states are defined in Table~\ref{table:states}
-  except state T which refers to the transition emissions.}\label{table:msddm_params}
-  \end{table}
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+%  \hline
+%  & \multicolumn{3}{c|}{Urea}                      & \multicolumn{3}{c|}{Ethylene Glycol} \\\hline
+%  State & H     & $\alpha_h$ & $\sigma$  & H    & $\alpha_h$ & $\sigma$ \\\hline
+%  1     & 0.10  & 1.79       & 0.034     & 0.09 & 1.68       & 0.045    \\
+%  2     & 0.06  & 1.80       & 0.033     & 0.09 & 1.75       & 0.037    \\
+%  3     & 0.11  & 1.88       & 0.030     & 0.11 & 1.86       & 0.030    \\
+%  4     & 0.10  & 1.95       & 0.027     & 0.04 & 1.91       & 0.028    \\
+%  5     & 0.19  & 1.34       & 0.048     & 0.15 & 1.40       & 0.062    \\
+%  6     & 0.15  & 1.45       & 0.040     & 0.11 & 1.52       & 0.040    \\
+%  7     & 0.15  & 1.61       & 0.032     & 0.05 & 1.60       & 0.040    \\
+%  8     & 0.11  & 1.71       & 0.028     & 0.05 & 1.74       & 0.030    \\
+%  T     & 0.34  & 1.42       & 0.036     & 0.37 & 1.44       & 0.045    \\\hline
+%  \end{tabular}
+%  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
+%  trajectories and then computed the average ensemble-averaged MSD of 10000 
+%  simulated trajectories. The states are defined in Table~\ref{table:states}
+%  except state T which refers to the transition emissions.}\label{table:msddm_params}
+%  \end{table}
 
@@
 
+  % /figures/msddm_state_probabilities.py
   \begin{figure}
@@
   \end{subfigure}
-  % BJC3: these need more data
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{URE_msddm.pdf}
-%  \caption{}\label{fig:MET_msddm}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{GCL_msddm.pdf}
-%  \caption{}\label{fig:ACH_msddm}
-%  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{MET_msddm.pdf}
+  \caption{}\label{fig:MET_msddm}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ACH_msddm.pdf}
+  \caption{}\label{fig:ACH_msddm}
+  \end{subfigure}
   \caption{MSDs predicted by the MSDDM significantly over-predict those

### 2019-10-22 LLC_Membranes/analysis/sfbm_parameters.py

@@ -59,6 +59,9 @@ class SFBMParameters(object):
         self.t = md.load(traj, top=gro)[start:end:step]
         print('Done!')
 
+        self.begin = start
+        self.end = end
+
         self.time = self.t.time / 1000  # time in nanoseconds
         self.dt = self.time[1] - self.time[0]  # time step
         self.nT = self.t.n_frames
@@ -209,7 +212,7 @@ class SFBMParameters(object):
                                                   spline_name=spline_name)
 
         self.partition = physical.partition(self.com, self.pore_centers, r, unitcell=self.t.unitcell_vectors,
-                                            spline=spline)
+                                            spline=spline, spline_range=(self.begin, self.end))
 
         if write_tcl:
             self.write_tcl()

### 2019-10-30 Ben_Manuscripts/stochastic_transport/Draft.tex
Getting simulations of concentration profiles working

@@
 
+  %BJC4: Not sure if I should start by commenting on the stationarity of the 
+  %solute trajectories. I talk about it when I start validating with the train/test procedure.
+
+%  \subsection{Stationarity of Solute Trajectories}\label{section:stationarity}
+%  %BJC4: Maybe re-theme the section: applicability of model
+%  
+%  Before applying the model, it is important to analyze the MD trajectories
+%  themselves in order to understand what conclusions one could reasonably to 
+%  draw by applying these models. 
+%  
+%  %BJC4: this might belong with validation.
+%  We observe that in many cases, the distribution of solutes within the membrane
+%  evolves slowly with time. We defined the perceived equilibration time point 
+%  for each solute based on the time at which the number of solutes inside the
+%  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
+%  solute behavior after equilibration on the $\mu$s timescale. In Table \_\_, we compare the MSD of the 
+%  solutes calculated using trajectory data from the first and second halves of the
+%  equilibrated simulation time. Ethylene glycol and methanol, show considerable
+%  differences in their MSDs. Although the MSD calculated from both halves of the 
+%  acetic acid trajectories are similar, their shapes are considerably different 
+%  (see SI). Urea is the only solute in this study that demonstrates satisfactory
+%  stationarity on the 5 $\mu$s timescale.
+%  
+%  The non-stationary behavior of each solute presents itself in different ways.
+%  On average, methanol molecules in the tails appear to be drifting further 
+%  away from the pore center with time. Ethylene glycol appears to experience an
+%  increased incidence of long trapping times. The partition of acetic acid 
+%  between the pores and tails oscillates slowly over time. These problems probably
+%  cannot be addressed without more simulation time or additional solute trajectories. 
+%  
+%  In light of these observations, we chose to demonstrate the performance and insights
+%  that could be gained from our models using all of solutes with complete data sets
+%  collected after the perceived equilibration time. However, we only use urea to 
+%  validate the model's predictive power and to estimate solute flux.
+%    
+%  There are a couple of ways to address this issue in the long term. The simplest
+%  approach is to run the MD simulations longer. This option is likely not feasible
+%  because the equilibration timescale in these systems is unknown for most of 
+%  the solutes in the study, even after consider computational effort. A more 
+%  sustainable approach, which would help screen any solute of interest, would 
+%  require us to learn the equilibrium distribution of solutes in the membrane
+
   \subsection{Anomalous Diffusion Modeling}\label{section:sFBM}
 
-  The evidence suggests that solutes in this system can be well-modeled by 
-  subordinated fractional Brownian motion. The solutes clearly perform jumps after periods of relative immobility
-  (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
+  The evidence suggests that solutes in this system can be well-modeled by subordinated
+  fractional Brownian motion. The solutes clearly perform jumps after periods of relative
+  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
   of jump lengths and power law distribution of dwell times are both characteristic of 
@@
   is common in crowded viscoelastic environments where motions are highly influenced by
-  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}.
+  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
+  The parameter estimates describing our 1 and 2 mode models are summarized in 
+  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}.
 
@@
   long dwell times in our simulations. (d) The hops are negatively correlated to their previous
-  hop. In combination (a) -- (d) support modeling solutes as subordinated fractional Brownian
+  hop. In combination, (a) -- (d) support modeling solutes as subordinated fractional Brownian
   motion. The behavior shown by urea in this figure is common to all solutes in this study.}\label{fig:anticorrelated_hops}
@@
   Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a better
-  job capturing the heavy tails and high density near 0 of the hop length distribution.
+  job capturing the somewhat heavy tails and high density near 0 of the hop length distribution.
   However, since there are no known exact simulation techniques for generating 
@@
   MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
-  comparison in Figures~\ref{fig:anomalous_msds_1mode} and Figure~\ref{fig:anomalous_msds_2mode}
-  respectively. Our anomalous diffusion trajectories have a significantly reduced 
-  uncertainty and lie well within the error bars of MD.
+  comparison in Figures~\ref{fig:anomalous_msds_1mode} and~\ref{fig:anomalous_msds_2mode}
+  respectively. 
+  %The MSD of AD trajectories modeled using a power law with an exponential 
+  %cut-off have a significantly reduced uncertainty and lie well within the error bars of MD.
 
@@
 
-  %BJC3: simulated anomalous diffusion --> SAD ? HMM kind of a downer
-  Simulated anomalous diffusion trajectories which draw from a L\'evy stable distribution
-  generally predict higher MSDs. The heavy tails of the distribution incorporate large
+  Simulated AD trajectories which draw from a L\'evy stable distribution generally 
+  predict higher MSDs. The heavy tails of the distribution incorporate large
   jumps more frequently into the trajectories. The only exception is that of ethylene
@@
   a near Gaussian distribution.
-
-  The model parameters for the 1 and 2 mode models tell stories about each solute's behavior. 
+  % BJC4: need to explain this somehow.
+
+  The model parameters for the 1 and 2 mode models tell stories about each solute's
+  behavior that help explain the difference between the MSDs of different solutes. 
   Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
@@
   value because it spends the majority of its time outside the pore region where collisions
-  with tails are frequent. Urea has the third highest MSD which is influenced primarily
-  by more frequent and long dwell times, indicated by lower values of $\alpha_d$ and 
+  with tails are frequent. Urea has the third highest MSD that is primarily a consequence of
+  more frequent and long dwell times, indicated by lower values of $\alpha_d$ and 
   $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
@@
   structurally similar molecules, both planar with two heavy atoms attached to a 
-  carbonyl group. Their small size and rigid shape may allow them to slip through 
-  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
-  larger jumps to escape traps.
+  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
+  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
+  to make larger jumps to escape traps.
 
@@
 
-  We further validated our models by training the parameters on half of the 
-  equilibrated trajectories and then using them to predict the MSD calculated
-  from the alternate half of the trajectories. We trained on both the first
-  and second half of the data. At equilibrium, the parameter estimates should 
-  be the same, within error, for either portion of the data used for training.
+  \subsubsection{Model validation on stationary trajectories}\label{section:sfbm_validation}
+
+  We evaluated the predictive capabilities of the AD modeling approach by training
+  the model parameters on the first half of the equilibrated MD trajectory data
+  then comparing the MSD calculated from AD model realizations to the MSD calculated
+  from the second half of the equilibrated MD trajectory data. This metric is
+  only meaningful if the ensemble of solute trajectories is stationary.
+
+  We observe that in many cases, the distribution of solutes within the membrane
+  evolves slowly with time. We defined the perceived equilibration time point 
+  for each solute based on the time at which the number of solutes inside the
+  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
+  solute behavior after equilibration, on the $\mu$s timescale. In Table~\ref{table:stationarity},
+  we compare the MSD of the solutes calculated using trajectory data from the 
+  first and second halves of the equilibrated simulation time. Ethylene glycol 
+  and methanol show considerable differences in their MSDs. Urea and acetic acid
+  appear to demonstrate satisfactory stationarity on the 5 $\mu$s timescale. The
+  shapes of their MSDs curves are also very similar (see Figure~\ref{S-fig:msd_comparison}
+  of the Supporting Information).
 
@@
   \centering
-  \begin{tabular}{|M{1.75cm}|M{1cm}|M{1.65cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|}
+  \begin{tabular}{|c|c|c|}
   \hline
-  \multirow{2}{*}{Solute}&\multirow{2}{*}{Modes}&\multirow{2}{*}{Model}&\multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{4-7}
-                              &                   &        & MD MSD                & Prediction & MD MSD               & Prediction \\\hline
-  \multirow{4}{*}{Urea}       & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.43 (1.11, 1.76)}&0.31 (0.28, 0.35)&\multirow{4}{*}{1.43 (1.11, 1.77)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
-                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-                              &                   &sFLMcut&                         &            &                     &            \\\hline
-                              & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.03 (0.79, 1.29)}        &            &\multirow{4}{*}{1.03 (0.77, 1.30)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-  Ethylene                    &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
-  Glycol                      &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-                              &                   &sFLMcut&                         &            &                     &            \\\hline
-  \multirow{4}{*}{Methanol}   &\multirow{2}{*}{1} &sFBMcut&\multirow{4}{*}{1.06 (0.69, 1.36)}        &            &\multirow{4}{*}{1.06 (0.67, 1.37)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-                              &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
-                              &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-                              &                   &sFLMcut&                         &            &                     &            \\\hline
-  \multirow{4}{*}{Acetic Acid}& \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{0.35 (0.28, 0.45)}&0.31 (0.28, 0.35)&\multirow{4}{*}{0.35 (0.26, 0.47)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
-                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-                              &                   &sFLMcut&                         &            &                     &            \\\hline
+  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
+                           & First Half       & Second Half      \\\hline
+  Urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
+  Ethylene Glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
+  Methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
+  Acetic Acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
+
   \end{tabular}
-  \caption{}\label{table:sFBM_train}
+  \caption{In order to be considered stationary, the MSD of the ensemble of solute trajectories
+  should be the same independent of the portion of equilibrated trajectory that is
+  analyzed. The MSD values in this table are averages taken after a 500 ns time lag, 
+  calculated independently from the first and second halves of the equilibrated
+  solute trajectories. Urea and acetic acid both appear to satisfy the stationarity
+  criteria, while ethylene glycol and methanol show significantly smaller MSDs 
+  when calculated from the second half of the equilibrated trajectories.}\label{table:stationarity}
   \end{table}
+
+  The non-stationary behavior of ethylene glycol and methanol present themselves
+  in different ways. On average, methanol molecules in the tails appear to be 
+  drifting further away from the pore center with time. Methanol's small size 
+  significantly increases the volume of accessible structural space. Ethylene 
+  glycol appears to experience an increased incidence of long trapping times. 
+  These problems probably cannot be addressed without more simulation time or 
+  additional solute trajectories.
+
+  Using the approach described above, we validated our 1 and 2 mode models with
+  urea and acetic acid, since their trajectories appear stationary. The 
+  resultant MSD plots are shown in Figure~\ref{fig:train_test}.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
+  \caption{Urea (1 mode)}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
+  \caption{Urea (2 modes)}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
+  \caption{Acetic acid (1 mode)}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
+  \caption{Acetic acid (2 modes)}
+  \end{subfigure} 
+  \caption{The MSD curves predicted by the AD model trained on the first half 
+  of the equilibrated data closely reproduce the MSD curves generated from the 
+  second half of the equilibrated solute data.}\label{fig:train_test}
+  \end{figure}
+
+  The models reasonably predict the MSD of the second half of the solute 
+  trajectories based on parameters generated from the first half. This success
+  provides increased confidence in our ability to generate useful predictions
+  of long time scale solute behavior
+
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{|M{1.75cm}|M{1cm}|M{1.65cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|}
+%  \hline
+%  \multirow{2}{*}{Solute}&\multirow{2}{*}{Modes}&\multirow{2}{*}{Model}&\multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{4-7}
+%                              &                   &        & MD MSD                & Prediction & MD MSD               & Prediction \\\hline
+%  \multirow{4}{*}{Urea}       & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.43 (1.11, 1.76)}&0.31 (0.28, 0.35)&\multirow{4}{*}{1.43 (1.11, 1.77)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+%                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
+%                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+%                              &                   &sFLMcut&                         &            &                     &            \\\hline
+%                              & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.03 (0.79, 1.29)}        &            &\multirow{4}{*}{1.03 (0.77, 1.30)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+%  Ethylene                    &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
+%  Glycol                      &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+%                              &                   &sFLMcut&                         &            &                     &            \\\hline
+%  \multirow{4}{*}{Methanol}   &\multirow{2}{*}{1} &sFBMcut&\multirow{4}{*}{1.06 (0.69, 1.36)}        &            &\multirow{4}{*}{1.06 (0.67, 1.37)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+%                              &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
+%                              &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+%                              &                   &sFLMcut&                         &            &                     &            \\\hline
+%  \multirow{4}{*}{Acetic Acid}& \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{0.35 (0.28, 0.45)}&0.31 (0.28, 0.35)&\multirow{4}{*}{0.35 (0.26, 0.47)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+%                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
+%                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
+%                              &                   &sFLMcut&                         &            &                     &            \\\hline
+%  \end{tabular}
+%  \caption{}\label{table:sFBM_train}
+%  \end{table}
 
@@
 
-  To create an MSDDM for each solute, we generated emission distributions for
-  fluctuations within each state and transitions between states. There are not
-  enough consecutive observations of each type of transition with which to study
-  their individual correlation structures so we grouped all transition distributions
+  To create an MSDDM for each solute, we determined the state sequence of each 
+  solute solute trajectory and then generated emission distributions for fluctuations
+  within each state as well as transitions between states. There are not enough 
+  consecutive observations of each type of transition with which to study their 
+  individual correlation structures so we grouped all transition distributions
   into a single distribution and measured the correlation of the series of all 
@@
 
-  We observe correlated emissions drawn from L\'evy stable distributions.
-  The deviation of the emission distributions from Gaussian behavior is far more pronounced
+  We observe correlated emissions drawn from L\'evy stable distributions. The 
+  deviation of the emission distributions from Gaussian behavior is far more pronounced
   than that seen in the hop length distributions of the previous section, therefore we 
@@
   are tabulated in Table~\ref{table:msddm_params}.
+
   %MRS4: might this work better visually?  Table in SI, figure here?
-  %BJC4: Somehow I'd need to fit 108 pieces of data into a figure
+  %BJC4: Are you talking about the table after this figure? Somehow I'd need to fit 108 pieces of data into a single figure
   \begin{figure}
@@
   & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
-  State & H     & $\alpha$ & $\sigma$ & H    & $\alpha$ & $\sigma$   & H     & $\alpha$ & $\sigma$ & H    & $\alpha$ & $\sigma$ \\\hline
+  State & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$   & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$ \\\hline
   1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045      & 0.11  & 1.56     & 0.052    & 0.10 & 1.78     & 0.035    \\
@@
   \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
-  trajectories and then computed the average ensemble-averaged MSD of 1000 
-  simulated trajectories. The states are defined in Table~\ref{table:states}
-  except state T which refers to the transition emissions.}\label{table:msddm_params}
+  trajectories and used them to generate realizations of our MSDDM model. The states
+  are defined in Table~\ref{table:states} except state T which describes the transition
+  emissions.}\label{table:msddm_params}
   \end{table}
@@
   anti-correlated as indicated by their consistently low Hurst parameters.
-  The Hurst parameters for transitional emissions are 2-9 times higher than
-  emissions from trapped states. The value of $\alpha_h$ for transition 
+  Perfectly anti-correlated motion ($H$=0) results in no contribution to the solute's
+  MSD. Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
+  trapping mechanisms. Highly anti-correlated behavior in the pores in the absence of
+  any trapping mechanism is likely caused by collisions with monomer head groups 
+  within the pore region. The Hurst parameters for transitional (T) emissions are 2-18 times higher 
+  than emissions from trapped states. The value of $\alpha_h$ for transition 
   emissions is also relatively low giving higher probabilities to larger hops.
 
-  As solutes are influenced by more trapping effects, the width of the hop length
-  distribution, $\sigma$, decreases while its L\'evy index increases. Treating the
-  tail and pore regions independently, $\sigma$ is largest and $\alpha_h$ is lowest
-  when solutes are not hydrogen bonding or associating with sodium (states 1 and 5).
+  As solutes are influenced by more trapping effects simultaneously, the width of
+  the hop length distribution, $\sigma$, decreases while its L\'evy index increases.
+  Treating the tail and pore regions independently, $\sigma$ is largest and $\alpha_h$
+  is smallest when solutes are not hydrogen bonding or associating with sodium (states 1 and 5).
   Solutes are free to move and take occasionally large hops. The smallest $\sigma$
@@
   of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
-  Urea and ethylene glycol spend 56\% and 44\% of their time in the tails
-  respectively. Urea's compact and flat structure allows it to more easily 
+  Urea and acetic acid spend slightly more than half their time in the tails (56\% and 62\% 
+  of their time respectively) while ethylene glycol spends about 44\% of its time in the tails.
+  Urea and acetic acid's compact and flat structure allows it to more easily 
   partition into the tails while ethylene glycol prefers the pore region due to 
-  its two hydrophilic hydroxyl groups.
+  its two hydrophilic hydroxyl groups. Meanwhile methanol spends 91 \% of its 
+  time in the tails likely due to its small size.
 
@@
   Urea spends the largest fraction of its time trapped via association with sodium ions.
-  It does so 31\% of the total time while in the tails (state 3) and 21\%
-  of the total time while in the pores (state 7). The electron-dense and 
-  unshielded oxygen atom of urea's carbonyl group are prone to associate 
-  with positively charged sodium ions. The nitrogen atoms of urea are only
-  weak hydrogen bond donors.
+  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
+  total time while in the pores (state 7). The electron-dense and unshielded oxygen
+  atom of urea's carbonyl group is prone to associate with positively charged sodium
+  ions. The nitrogen atoms of urea are only weak hydrogen bond donors.
 
@@
   head groups and the ether linkages between the head groups and monomer tails.
+
+  Methanol spends most of its time unbound in the tail region (state 1) and spends a 
+  significant portion of time hydrogen bonded to while in the tail regions.
+  Most of the tail region hydrogen bonds are donated from methanol to the ether
+  linkages between the monomer head groups and tails.
+
+  Finally, acetic acid spends the majority of it's time hydrogen bonding in and out
+  of the pore.
 
@@
 
+  \subsection{Predicting solute flux}\label{section:mfpt}
+
+  In this section, we use our most promising models to predict solute flux 
+  through a theoretical 50 nm channel. For our comparisons to MD, using a truncated
+  power law distribution is an obvious choice. However, given that extremely
+  long dwells are a rare event, it is possible that studying a much larger set of 
+  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
+  distributions, the generality of L\'evy stable distributions is powerful, but the
+  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
+  accuracy and computational tractability. Treating the dynamics as fractional 
+  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is 
+  well below 2.
+
+  Choosing which model to use for long timescale projections is not entirely obvious
+  without experimental data to compare with.
+
 %  We projected the long timescale behavior using this model.

### 2019-10-30 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Getting simulations of concentration profiles working

@@
 
+  \section{Stationarity of Solute Trajectories}\label{section:msd_comparison}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
+  \caption{Urea}\label{fig:URE_MSD_halves}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
+  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
+  \caption{Methanol}\label{fig:MET_MSD_halves}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
+  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
+  \end{subfigure}
+  \caption{The ensemble of solute trajectories may be stationary if the MSD
+  calculated from different portions of the trajectory are the same. Here we
+  plot the MSD calcluated up to a 500 ns time lag of the first and second
+  halves of the equilibrated solute trajctories. Urea and acetic acid have
+  similar MSDs, providing evidence of stationarity, while the MSDs of 
+  ethylene glycol and methanol are different.}\label{fig:msd_comparison}
+  \end{figure}
+
   \section{2-state MSDDM parameters}\label{section:simple_msddm_params}
@@
 
+  \section{Mean first passage time simulations}\label{section:mfpt}
+
+  We validated our approach to simulating trajectory realizations by testing
+  it against analytical solutions to the mean first passage time of a Brownian
+  particle with 2 absorbing boundaries.
+
+  % equations here 
+  % Analytical CDF: https://journals.aps.org/pre/pdf/10.1103/PhysRevE.73.046104
+  % Analytical MFPT https://journals.aps.org/pre/pdf/10.1103/PhysRevE.62.6065
+  % Figures: mfpt_pdf.pdf and mfpt_cdf.pdf
+
   \clearpage

### 2019-10-30 LLC_Membranes/analysis/sfbm_parameters.py

@@ -32,7 +32,7 @@ class DistributionError(Exception):
 
 class SFBMParameters(object):
 
-    def __init__(self, traj, gro, res, start=0, end=-1, step=1, ma=False, nmodes=1):
+    def __init__(self, traj, gro, res, start=0, end=-1, step=1, ma=False, nmodes=1, train=False):
         """ Using an MD trajectory, calculate fit parameters for the dwell time distribution and hop length distribution
 
         :param traj: name of MD trajectory (GROMACS .xtc or .trr)
@@ -44,6 +44,7 @@ class SFBMParameters(object):
         :param ma: calculate a moving average on the center of mass coordinate traces
         :param nmodes: number of modes to consider. 1 mode will treat all hops and dwells as being performed in the \
         same environment. 2 modes will treat hops and dwells in the tails versus pores differently.
+        :param train: if not False, provide a set of solute indices on which to train parameters.
 
         :type traj: str
         :type gro: str
@@ -52,6 +53,7 @@ class SFBMParameters(object):
         :type end: int
         :type step: int
         :type nmodes: int
+        :type train: bool or list
         """
 
         # load trajectory
@@ -78,6 +80,10 @@ class SFBMParameters(object):
         print('Calculating centers of mass...', end='', flush=True)
         self.com = physical.center_of_mass(self.pos, self.mass)  # center of mass of residues
         print('Done!')
+
+        if train:
+            self.com = self.com[:, train, :]
+            print(self.com.shape)
 
         # plot z-coordinate trace
         # for i in range(self.com.shape[1]):

### 2019-10-30 LLC_Membranes/timeseries/forecast_ctrw.py

@@ -104,7 +104,7 @@ if __name__ == "__main__":
     else:
 
         sys = SFBMParameters(fit['trajectory'], fit['gro'], fit['residue'], start=fit['begin'], end=fit['end'],
-                             step=fit['step'], ma=fit['ma'], nmodes=fit['nmodes'])
+                             step=fit['step'], ma=fit['ma'], nmodes=fit['nmodes'], train=fit['train'])
 
         # only need this if 2 mode I think
         sys.calculate_solute_partition(spline=fit['spline'], membrane_residue=fit['membrane_residue'],

### 2019-10-30 LLC_Membranes/timeseries/truncated_levy_database.py

@@ -19,7 +19,7 @@ from LLC_Membranes.timeseries.flm_sim_params import TruncateLevy
 alphas = np.linspace(1, 2, 10)
 H = np.linspace(0.0, 0.5, 11)
 trunc = np.linspace(1, 100, 10)
-scale = 0.35
+scale = 0.36
 nrealizations = 10
 load = False
 append = True

### 2019-11-21 Ben_Manuscripts/stochastic_transport/Draft.tex
Getting peak of passage time distributions

@@
 
-  \subsection{Solute Flux}
+  \subsection{Mean First Passage Time}
+
+  We used the mean first passage time (MFPT) in order to quantify how long it would take a 
+  typical particle, parameterized with the above models, to travel across a membrane pore
+  of length $L$. To measure this quantity, we simulated realizations of 10000 particle 
+  trajectories, started at the pore entrance ($z=0$). In the case of uncorrelated hops, one
+  can continuously draw from the hop length distribution until $z \geq L$ (Or $-L$ for 
+  the sake of computational efficiency). The length of time between the last time the 
+  particle crossed $z=0$ and the end of the trajectory gives a single passage time. 
+  When particle hops are correlated, as they are in all cases of this work, we cannot 
+  continuously construct the particle trajectories. Rather, we must generate trajectories
+  of length $n$ and measure the length of the sub-trajectory which traverses from $0$ 
+  to $L$ without becoming negative. It is important to choose a value of $n$ sufficiently
+  large that all trajectories reach $L$, or else the mean first passage time will 
+  be underestimated.
+
+  Our definition of the mean first passage time differs from more standard treatments.
+  The setup of our system is consistent with a one dimensional interval with two absorbing 
+  boundaries. In the absence of an external force and a constant diffusion coefficient, $D$, 
+  the mean first passage time is simply:
+  \begin{equation}
+  T = \frac{z_0(L - z_0)}{2D}
+  \end{equation}
+  where $z_0$ is the initial position of particle trajectories.~\cite{gitterman_mean_2000}
+  Of course that implies a conventional MFPT of 0 since particles overwhelmingly exit the
+  pore at $z=0$. Therefore, we chose only to include trajectories in the MFPT calculation 
+  which cross the boundary at $L$. We are unaware of an analytical form of the MFPT or 
+  the distribution of passage times describing our system even in the simplest case of 
+  Brownian increments.
+
+  In the absence of an analytical equation for the MFPT, we instead report the location of
+  the peak of the passage time distribution. This has the added advantage of treating
+  cases where the passage time distribution diverges and no mean exists. While we will
+  call the peak in the distribution the MFPT, it is important to recognize that this 
+  value is more representative of a typical passage time rather than a mean.
+
+  % BJC: concentration profile stuff
+%  One would then segment the trajectory
+%  each time it crosses $0$ and reflect all of the negative trajectories. The ensemble of
+%  trajectories is consistent with the fraction of partic
 

### 2019-11-22 Ben_Manuscripts/stochastic_transport/Draft.tex
Adjusting visualizations

@@
 
-  \subsection{Mean First Passage Time}
+  \subsection{Mean First Passage Time}\label{method:mfpt}
 
@@
 
-  \subsection{Predicting solute flux}\label{section:mfpt}
-
-  In this section, we use our most promising models to predict solute flux 
-  through a theoretical 50 nm channel. For our comparisons to MD, using a truncated
-  power law distribution is an obvious choice. However, given that extremely
-  long dwells are a rare event, it is possible that studying a much larger set of 
-  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
-  distributions, the generality of L\'evy stable distributions is powerful, but the
-  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
-  accuracy and computational tractability. Treating the dynamics as fractional 
-  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is 
-  well below 2.
-
-  Choosing which model to use for long timescale projections is not entirely obvious
-  without experimental data to compare with.
+  \subsection{Solute Mean First Passage Times}\label{section:mfpt}
+
+  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
+  diffusion model in order to demonstrate how one can use its realizations in
+  order to calculate the MFPT (section~\ref{method:mfpt}) of solutes given model 
+  parameters extracted from MD simulations. Any approach which allows one to 
+  generate realizations of solute trajectories can be used in place of the AD model.
+
+  In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
+  with pore length. We fit a curve of the form $cL^{\alpha}$ to the curves in order
+  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
+  to the solute MSDs which is consistent with longer passage times for solutes that
+  progres through the pores more slowly.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
+  \caption{}\label{fig:mfpt_curves_regular}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
+  \caption{}\label{fig:mfpt_curves_brownian}
+  \end{subfigure}
+  \caption{}\label{fig:mfpt_curves}
+  \end{figure}
+
+  The growth exponent is inversely related to the hurst parameter. In 
+  Figure~\ref{fig:mfpt_curves_brownian}, we removed the correlation structure (set
+  $H$=0.5) from AD trajectory realizations so that all hops were uncorrelated.
+  Regardless of the parameters of the dwell time distribution, the growth 
+  exponent is always about 2, the same value that we observe for Brownian 
+  motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the Supporting 
+  Information).
+
+  Comparison of Figures~\ref{fig:mfpt_curves_regular} and~\ref{fig:mfpt_curves_brownian}
+  highlights that the Hurst parameter plays a major role in
+
+  The correlation between hops signficantly
+
+  %BJC: can make design suggestions by trying to decrease anticorrelation by x
+
+%  In this section, we use our most promising models to predict solute flux 
+%  through a theoretical 50 nm channel. For our comparisons to MD, using a truncated
+%  power law distribution is an obvious choice. However, given that extremely
+%  long dwells are a rare event, it is possible that studying a much larger set of 
+%  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
+%  distributions, the generality of L\'evy stable distributions is powerful, but the
+%  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
+%  accuracy and computational tractability. Treating the dynamics as fractional 
+%  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is 
+%  well below 2.
+%  
+%  Choosing which model to use for long timescale projections is not entirely obvious
+%  without experimental data to compare with.
 
@@
   %MRS4: I willō track down the PRF grant number (if typical)
-  This work was supported in part by the ACS Petroleum Research Fund grant XXXXXX 
+  This work was supported in part by the ACS Petroleum Research Fund grant \#59814-ND7
   and the Graduate Assistance in Areas of National Need (GAANN)

### 2019-11-22 LLC_Membranes/setup/surfaces.py

@@ -70,7 +70,7 @@ def gridgen(surf, low, high, n, c=0, tol=0.01):
     y = np.linspace(low, high - bin_size, n)
     z = np.linspace(low, high - bin_size, n)
 
-    if surf.lower() == 'ia3d' or surf.lower() == 'gyroid':
+    if surf.lower() in ['ia3d', 'gyroid']:
 
         gyro = gyroid([x[:, None, None], y[None, :, None], z[None, None, :]], high - low)
 
@@ -86,7 +86,7 @@ def gridgen(surf, low, high, n, c=0, tol=0.01):
 
         grid = gyro_eval[:count_gyro, :]
 
-    elif surf.lower() == 'pn3m' or surf.lower() == 'schwarzd':
+    elif surf.lower() in ['pn3m', 'schwarzd', 'diamond']:
 
         schwarz = SchwarzD([x[:, None, None], y[None, :, None], z[None, None, :]], high - low)
         schwarz_eval = np.zeros([n**3, 3])
@@ -139,13 +139,13 @@ def gradient(v, surf, period):
 
     n = 2*np.pi / period
 
-    if surf.lower() == 'ia3d' or surf.lower() == 'gyroid':
+    if surf.lower() in ['ia3d', 'gyroid']:
 
         a = n*np.cos(n*x)*np.cos(n*y) - n*np.sin(n*x)*np.sin(n*z)
         b = -n*np.sin(n*y)*np.sin(n*x) + n*np.cos(n*y)*np.cos(n*z)
         c = -n*np.sin(n*y)*np.sin(n*z) + n*np.cos(n*z)*np.cos(n*x)
 
-    elif surf.lower() == 'pn3m' or surf.lower() == 'schwarzd':
+    elif surf.lower() in ['pn3m', 'schwarzd', 'diamond']:
 
         a = n*np.cos(n*x)*np.sin(n*y)*np.sin(n*z) + n*np.cos(n*x)*np.cos(n*y)*np.cos(n*z) - n*np.sin(n*x)*np.sin(n*y)*np.cos(n*z) - n*np.sin(n*x)*np.cos(n*y)*np.sin(n*z)
         b = n*np.sin(n*x)*np.cos(n*y)*np.sin(n*z) - n*np.sin(n*x)*np.sin(n*y)*np.cos(n*z) + n*np.cos(n*x)*np.cos(n*y)*np.cos(n*z) - n*np.cos(n*x)*np.sin(n*y)*np.sin(n*z)

### 2019-11-25 Ben_Manuscripts/stochastic_transport/Draft.tex
Updated parameters. New plots

@@
   typical particle, parameterized with the above models, to travel across a membrane pore
-  of length $L$. To measure this quantity, we simulated realizations of 10000 particle 
-  trajectories, started at the pore entrance ($z=0$). In the case of uncorrelated hops, one
-  can continuously draw from the hop length distribution until $z \geq L$ (Or $-L$ for 
+  of length $L$. To measure this quantity, we simulated 50000 realizations of particle 
+  trajectories, released at the pore entrance ($z=0$). In the case of uncorrelated hops, one
+  can continuously draw from the hop length distribution until $z \geq L$ (or $-L$ for 
   the sake of computational efficiency). The length of time between the last time the 
@@
   of length $n$ and measure the length of the sub-trajectory which traverses from $0$ 
-  to $L$ without becoming negative. It is important to choose a value of $n$ sufficiently
-  large that all trajectories reach $L$, or else the mean first passage time will 
-  be underestimated.
-
-  Our definition of the mean first passage time differs from more standard treatments.
-  The setup of our system is consistent with a one dimensional interval with two absorbing 
-  boundaries. In the absence of an external force and a constant diffusion coefficient, $D$, 
-  the mean first passage time is simply:
+  to $L$ without becoming negative.
+  %BJC4: below is only necessary if you the mean of the distribution exists.
+  %It is important to choose a value of $n$ sufficiently
+  %large that all trajectories reach $L$, or else the mean first passage time will 
+  %be underestimated.
+
+  Our definition of the MFPT differs from more standard treatments. The setup of our 
+  system is consistent with a one dimensional interval with two absorbing boundaries. In
+  the absence of an external force and with a constant diffusion coefficient,
+  $D$, the MFPT is simply:
   \begin{equation}
@@
   the distribution of passage times describing our system even in the simplest case of 
-  Brownian increments.
-
+  Brownian increments. %BJC4: still digging for an analytical solution. Rich said the 
+  %'marathon' runner problem might give a solution. It may be the same as the distribution
+  % of runners crossing the finish line
+
+  %BJC4: I'm not sure the best way to get the peak
   In the absence of an analytical equation for the MFPT, we instead report the location of
@@
   CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
-  correlation between hops suggests a fractional diffusion process is subordinate to the
+  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
   CTRW. We believe the subordinated process is FBM because its analytical correlation 
@@
   The parameter estimates describing our 1 and 2 mode models are summarized in 
-  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}.
+  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} (also trying it out in 
+  Figures~\ref{fig:radars} and~\ref{fig:radars_nolines})
 
@@
 
+  %BJC4: another way to visualize data
+  %BJC4: I think these are kind of hard to read. Can't really see any trends. Open to other
+  %ideas.
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{1mode_radar.pdf}
+  \caption{}\label{fig:1mode_radar}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{2mode_radar.pdf}
+  \caption{}\label{fig:2mode_radar}
+  \end{subfigure}
+  \caption{Another way to visualize Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}}\label{fig:radars}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
+  \caption{}\label{fig:1mode_radar}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\linewidth]{2mode_radar_nolines.png}   % for some reason it has trouble saving this as a PDF
+  \caption{}\label{fig:2mode_radar}
+  \end{subfigure}
+  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
+  \end{figure}
+
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
+%  \caption{}\label{fig:1mode_radar_nolines}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{2mode_radar_nolines.pdf}
+%  \caption{}\label{fig:2mode_radar_nolines}
+%  \end{subfigure}
+%  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
+%  \end{figure}
+
   Using the parameters in Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}
@@
   %MRS4: might this work better visually?  Table in SI, figure here?
-  %BJC4: Are you talking about the table after this figure? Somehow I'd need to fit 108 pieces of data into a single figure
   \begin{figure}
@@
   \end{table}
+
+  %BJC4: better visualization scheme
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{H_v_state.pdf}
+  \caption{}\label{fig:H_v_state}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{alpha_v_state.pdf}
+  \caption{}\label{fig:alpha_v_state}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
+  \caption{}\label{fig:sigma_v_state}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{state_probabilities.pdf}
+  \caption{}\label{fig:state_probabilities}
+  \end{subfigure}
+  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
+  trajectories and used them to generate realizations of our MSDDM model. The states
+  are defined in Table~\ref{table:states} except state T which describes the transition
+  emissions.}\label{fig:msddm_parameters}
+  \end{figure}
+
 %  
@@
   % /figures/msddm_state_probabilities.py
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{state_probabilities.pdf}
-  \caption{The probability of finding urea or ethylene glycol in a given state.}\label{fig:state_probabilities}
-  \end{figure}
+  %BJC4: combined with previous figure.
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{state_probabilities.pdf}
+%  \caption{The probability of finding urea or ethylene glycol in a given state.}\label{fig:state_probabilities}
+%  \end{figure}
+%
 
@@
   to the solute MSDs which is consistent with longer passage times for solutes that
-  progres through the pores more slowly.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
-  \caption{}\label{fig:mfpt_curves_regular}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
-  \caption{}\label{fig:mfpt_curves_brownian}
-  \end{subfigure}
-  \caption{}\label{fig:mfpt_curves}
-  \end{figure}
-
-  The growth exponent is inversely related to the hurst parameter. In 
+  progress through the pores more slowly.
+
+  The growth exponent is inversely related to the hurst parameter, $H$. In 
   Figure~\ref{fig:mfpt_curves_brownian}, we removed the correlation structure (set
@@
 
+  % BJC5: I'm not sure the best way to calculate statistics on this. Since I don't know
+  % the density function of the mean first passage time distribution, I use bins to 
+  % to locate the peaks. So the error bars are dependent on the bin width. 
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
+  \caption{Correlated Hops}\label{fig:mfpt_curves_regular}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
+  \caption{Uncorrelated Hops}\label{fig:mfpt_curves_brownian}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{frac_pore.pdf}  % This figure might fit in earlier
+  \caption{}\label{fig:frac_pore}
+  \end{subfigure}
+  \caption{(a) We fit the MFPT versus pore length to a function of the form $cL^{\alpha}$. 
+  The MFPT grows super-linearly with increasing pore length. Solutes with lower MSDs have
+  higher MFPTs. (b) If we remove correlation between hops, the MFPTs reduce significantly
+  and the growth exponent stays constant at 2 for all solutes independent of dwell
+  distribution parameters. Higher degrees of anti-correlation (lower $H$) lead to higher
+  growth exponents. (c) Solutes that spend a large fraction of their time in the tails tend
+  to have larger Hurst parameters.}\label{fig:mfpt_curves}
+  \end{figure}
+
   Comparison of Figures~\ref{fig:mfpt_curves_regular} and~\ref{fig:mfpt_curves_brownian}
-  highlights that the Hurst parameter plays a major role in
-
-  The correlation between hops signficantly
+  highlights that anti-correlation between hops plays a major role in solute passage times.
+  With a pore length of 50 nm, the MFPT of the fasted moving solute, ethylene glycol is 
+  c.a. 5 times higher with versus without anti-correlated hops. The MFPTs of the slowest
+  moving solute, acetic acid, are about 16 times higher by the same comparison. This 
+  difference will only grow with increasing pore length.
+
+  In Figure~\ref{fig:frac_pore}, we show that solutes which spend more time in the tails
+  tend to have lower Hurst parameters. The densely packed, viscoelastic alkane chains 
+  bounce solutes between them, severely limiting their mobility. Designing LLC membranes
+  that can control or prevent the partition of solutes into the tails may offer the highest
+  returns on membrane performance.
 

### 2019-11-25 Ben_Manuscripts/stochastic_transport/figures/ergodicity.py

@@ -1,0 +1,58 @@
+#!/usr/bin/env python
+
+from LLC_Membranes.analysis.msd import Diffusivity
+from LLC_Membranes.llclib import file_rw
+import matplotlib.pyplot as plt
+import numpy as np
+
+res = "URE"
+gro = "em.gro"
+traj = "5ms_nojump.xtc"
+directory = "/home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/%s/10wt" % res
+first_frame = {"URE": 2000, "GCL": 2400}
+nboot = 200
+fracshow=0.4
+dt = 0.5
+load = True
+stationarity = False 
+
+if load:
+	msd = file_rw.load_object('msd.pl')
+else:
+	msd = Diffusivity('%s/%s' % (directory,traj), '%s/%s' % (directory, gro), 'z', begin=first_frame[res], residue=res)
+	file_rw.save_object(msd, 'msd.pl')
+
+
+if stationarity:
+	p = msd.stationarity(axis=2)
+	print('Probability that time series is non-stationary:')
+	for i, pvalue in enumerate(p):
+		print('Trajectory %d: %.2f' % (i + 1, pvalue))
+
+msd.calculate()
+#eb = msd.ergodicity_breaking_parameter()
+#plt.plot(eb)
+#plt.show()
+#exit()
+
+msd.bootstrap(nboot, fit_line=False)
+
+end = int(fracshow * msd.time.size)
+t = np.arange(end) * dt
+
+plt.plot(t, msd.MSD_average[:end], label='Time Averaged MSD')
+plt.fill_between(t, msd.MSD_average[:end] + msd.limits[0, :end], msd.MSD_average[:end] - msd.limits[1, :end], alpha=0.7)
+
+msd.calculate(ensemble=True)
+msd.bootstrap(nboot, fit_line=False)
+plt.plot(t, msd.MSD_average[:end], label='Ensemble Averaged MSD')
+plt.fill_between(t, msd.MSD_average[:end] + msd.limits[0, :end], msd.MSD_average[:end] - msd.limits[1, :end], alpha=0.7)
+
+plt.legend(fontsize=14)
+plt.show()
+#reduce object size and save
+#MD_MSD.t = None
+#MD_MSD.com = None
+#file_rw.save_object(MD_MSD, '%s_msd.pl' % res)
+
+

### 2019-11-25 Ben_Manuscripts/stochastic_transport/figures/gaussian_levy_comparison_anomalous.py

@@ -1,0 +1,45 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+from LLC_Membranes.analysis.sfbm_parameters import SFBMParameters
+from LLC_Membranes.llclib import file_rw
+from scipy.stats import levy_stable, norm
+import matplotlib.pyplot as plt
+import numpy as np
+
+res = 'GCL'
+path = "/home/bcoscia/Documents/Gromacs/Transport/NaGA3C11/%s/10wt/forecast_%s_1state.pl" % (res, res)
+states = file_rw.load_object(path)
+
+hops = ['Gaussian', 'Levy']
+
+all_hops = []
+
+for h in states.hop_lengths:
+        all_hops += h[0]
+
+plt.hist(all_hops, bins=50, color='xkcd:blue', alpha=0.6, density=True)
+x = np.linspace(-1.5, 1.5, 500)
+
+for h in hops:
+	states.fit_distributions(plot=False, show=False, hop_distribution=h, nboot=10)
+
+	if h == 'Gaussian':
+                mean_sigma = np.mean([p[1] for p in states.hop_parameters[0]])
+                mean_mu = np.mean([p[0] for p in states.hop_parameters[0]])
+                plt.plot(x, norm.pdf(x, loc=mean_mu, scale=mean_sigma), '--', lw=2, color='xkcd:orange', label='Gaussian PDF')
+	elif h == 'Levy':
+                mean_alpha = np.mean([p[0] for p in states.hop_parameters[0]])
+                mean_sigma = np.mean([p[2] for p in states.hop_parameters[0]])
+                mean_mu = np.mean([p[1] for p in states.hop_parameters[0]])
+                plt.plot(x, levy_stable.pdf(x, alpha=mean_alpha, beta=0, loc=mean_mu, scale=mean_sigma), '--', color='xkcd:green', label=r'L$\'{e}$vy PDF', lw=2)
+
+plt.gcf().get_axes()[0].tick_params(labelsize=14)
+plt.legend(fontsize=14)
+plt.ylabel('Probability Density', fontsize=14)
+plt.xlim(-1.5, 1.5)
+plt.tight_layout()
+plt.savefig('gaussian_levy_comparison_anomalous_%s.pdf' % res)
+plt.show()

### 2019-11-25 Ben_Manuscripts/stochastic_transport/figures/test_eb.py

@@ -1,0 +1,39 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+from LLC_Membranes.llclib import timeseries
+
+ntraj = 10 
+npoints = 10000
+fracshow = 0.2
+low_T = 100
+
+# make Brownian trajectories
+
+x = np.zeros([npoints, ntraj])
+for t in range(ntraj):
+	x[:, t] = np.cumsum(np.random.normal(size=npoints))
+
+msd = timeseries.msd(x[..., np.newaxis], 0)
+limits = timeseries.bootstrap_msd(msd, 200)
+
+msd_mean = msd.mean(axis=1)
+msd_mean_squared = np.square(msd_mean)
+
+mean_msd_variance = np.zeros_like(msd_mean)
+for i in range(low_T, npoints):
+	mean_msd_variance[i] = np.square(msd[i, :]).mean()
+
+eb = (mean_msd_variance - msd_mean_squared) / msd_mean_squared
+
+t = np.arange(npoints)
+end = int(fracshow * npoints)
+
+plt.plot(t[:end], msd_mean[:end])
+plt.fill_between(t[:end], msd_mean[:end] + limits[0, :end], msd_mean[:end] - limits[1, :end], alpha=0.7)
+
+plt.figure()
+plt.plot(t[low_T:], eb[low_T:])
+plt.show()
+

### 2019-11-26 Ben_Manuscripts/stochastic_transport/Draft.tex
Updates to figures + captions

@@
   %BJC4: another way to visualize data
-  %BJC4: I think these are kind of hard to read. Can't really see any trends. Open to other
-  %ideas.
+  %BJC4: I think these are kind of hard to read. Can't really see any trends.
   \begin{figure}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{2mode_radar_nolines.png}   % for some reason it has trouble saving this as a PDF
+  \includegraphics[width=\linewidth]{2mode_radar_nolines.eps}   % for some reason it has trouble saving this as a PDF (.eps doesn't show opacity)
   \caption{}\label{fig:2mode_radar}
@@
 %  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
+  \caption{$\mathcal{N}(\sigma) / L(\sigma, \alpha_h)$}\label{fig:1mode_AD_hops}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
+  \caption{$P(\alpha_d) / P_T(\alpha_d, \lambda)$}\label{fig:1mode_AD_dwells}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
+  \caption{$\gamma(H)$}\label{fig:hurst_barchart}
+  \end{subfigure}
+  \caption{The parameters of the 1 mode model reveal differences in solute
+	  dynamics. (a) We parameterized Gaussian ($\mathcal{N}(\sigma)$,
+	  parameters given by bars with white background) and L\'evy stable
+	  ($L(\sigma, \alpha_h)$, parameters given by bars with gray
+	  background) distributions to describe solute hop lengths. We assume
+	  the mean ($\mu$) to be zero for these distributions and there to be
+	  no skewness ($\beta=0$) in the L\'evy stable distributions. High
+	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
+	  hops. (b) We parameterized a pure power law ($P(\alpha_d)$, white
+	  background) and a truncated power law ($P_T(\alpha_d, \lambda)$, gray
+	  background) distribution to describe solute dwell times. Lower values
+	  of $\alpha_d$ lead to heavier power law tails and higher values of
+	  $\lambda$ truncate the distribution at lower dwell times.(c) Finally,
+	  we parameterized the hop autocorrelation function ($\gamma(H)$) to
+	  describe the degree of correlation between hops.  Higher values of
+	  $H$ display closer to Brownian behavior.
+	  }\label{fig:1mode_bar_charts}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_AD_hops.pdf}
+  \caption{$\mathcal{N}(\sigma) / L(\sigma, \alpha_h)$}\label{fig:2mode_AD_hops}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
+  \caption{$P(\alpha_d) / P_T(\alpha_d, \lambda)$}\label{fig:2mode_AD_dwells}
+  \end{subfigure}
+  \caption{The two mode model parameterizes solute behavior in the pores and
+	  tails separately. Mode 1 corresponds to solute behavior within 0.75
+	  nm of the pore center, the pore region, and mode 2 corresponds to
+	  behavior greater than or equal to 0.75 nm from the pore center, the
+	  tail region. (a) Generally, movement is much more restricted in the
+	  tail region shown by lower mode 2 $\sigma$ values for the Normal
+	  (white background) and L\'evy distributions (gray background). Values
+	  of $\alpha$ are significantly lower for urea and acetic acid meaning
+	  there is a larger probability that they will take large hops.
+	  (b) Dwell times are longer in in the tails. Lower values of
+	  $\alpha_d$ correspond to power laws with heavier tails and thus
+	  higher probabilities of long dwell times. There is no easily
+	  discernable trend in $\lambda$ of the truncated power law
+	  distribution (gray background).  Note that we used the same Hurst
+	  parameter for both modes due to a low number of sufficiently long
+	  sequences of hops in each mode. See Figure~\ref{fig:1mode_bar_charts}
+	  for descriptions of the parameters.
+  }\label{fig:2mode_bar_charts}
+  \end{figure}
 

### 2019-11-26 Ben_Manuscripts/stochastic_transport/Draft.tex
Edits

@@
   simulations. The anomalous diffusion model shows superior predictive performance, 
-  in many cases reproducing MD results well within error. Finally, we use the 
-  parameters of each model to identify specific differences in solute transport
-  behavior which can help suggest modifications that can be made to LLC membrane 
-  monomers in order to increase or reduce selectivity towards a specific solute
-  or class of solutes.
+  in many cases reproducing MD results well within error. Finally, we
+  demonstrate how one can use our models in order to calculate the mean
+  first passage time, a quantity related to solute flux, of a given
+  solute across a macroscopic-length pore. Overall this work makes
+  great strides towards understanding the relationship between
+  microscopic chemically-dependent solute motions and macroscopic membrane performance.
+
+  %Overall, this work the parameters of each model to identify specific differences
+  %in solute
+  %transport behavior which can help suggest modifications that can be
+  %made to LLC membrane monomers in order to increase or reduce
+  %selectivity towards a specific solute or class of solutes.
 
@@
   models yield predictions of diffusion coefficients and solute transport rates 
-  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
-  tracking approaches take us beyond continuum modeling and allow us to 
+  in nanoporous membranes.~\cite{paul_diffusive_1974} More recently, single particle 
+  tracking approaches have taken us beyond continuum modeling and allow us to 
   characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
@@
   timescale predictions. We are in need of a way of studying the collective motion
-  of a much larger set of solute over much longer timescales.
+  of a much larger set of solutes over much longer timescales.
 
@@
 
-  In this work, we use the output of our MD simulations to construct two new classes of 
+  In this work, we use the output of our MD simulations to construct two classes of 
   mathematical models which can predict membrane performance while providing quantitative 
@@
   %BJC4: added mention of the anomalous subdiffusion model we chose 
-  Our first modeling approach is based on the anomalous diffusion literature, 
+  Our first modeling approach is based on the anomalous diffusion (AD) literature, 
   applying the mathematical formalism describing subdiffusive transport to observed
@@
   First, we parameterized solute motion using a single set of parameters fit
-  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
+  to a hypothesized AD model. Second, we used a two-state approach
   by extracting two sets of model parameters calculated based on a solute's radial
@@
 %  to different states. 
-  That is the magnitudes of a solute's fluctuations from its average trapped 
+  That is, the magnitudes of a solute's fluctuations from its average trapped 
   position and the degree of correlation with its previous fluctuations is 
@@
   while in each trapped state as well as the equilibrium occupation of each trapping state.
-  It is possible to use the two models in tandem, the anomalous diffusion model to
+  It is possible to use the two models in tandem, the AD model to
   identify mechanisms, and the MSDDM to characterize mechanisms.
@@
   %BJC4: new
-  We find that the sFBM anomalous diffusion model does the best job of reproducing
-  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
-  how one could predict solute flux through a theoretical pore of with an 
-  experimentally relevant length.
+  We find that the AD model does the best job of reproducing
+  simulation behavior of all solutes studied. Therefore, we use it to
+  demonstrate how one could predict the mean first passage time (MFPT) through
+  a theoretical pore with an experimentally relevant length. We show that the
+  MFPT grows super-linearly with pore length and that the associated growth
+  exponent increases as solute motion becomes more anti-correlated
 
@@
   where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
-  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
+  diffusion coefficient. We only calculate the MSD with respect to the solutes' center of
   mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
-  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 0$ 
+  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
   are characteristic of Brownian and superdiffusive motion respectively.
@@
   % In fact, the longest dwell time observed by any solute in this study is X. 
-  In order to directly compare our anomalous diffusion model to finite-length MD 
+  In order to directly compare our AD model to finite-length MD 
   trajectories we may need to bound the dwell time distribution. We do this by adding 
@@
   We observe different dynamical behavior when solutes move while inside 
-  the pore versus while in the tail region. This inspired two anomalous diffusion 
+  the pore versus while in the tail region. This inspired two AD 
   models of varying complexity. We created a simple, single mode model with a single 
@@
   % BJC3: will need to modify this text to reflect different lengths of simulations
-  For each solute, we simulated 10,000 anomalous diffusion trajectories of length
+  For each solute, we simulated 10,000 AD trajectories of length
   $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
@@
   %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
-  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
-  with corresponding 95\% confidence intervals.
-  When simulating 2 mode models, we determined the state sequence based on random 
-  draws weighted by the appropriate row of the probability transition matrix. We 
-  drew hops and dwells based on the current state of the system. Since we calculated
-  the transition probabilities from a finite data set, they have an associated 
-  uncertainty which we 
+  We reported the time-averaged MSD up to 1000 ns time lags with corresponding
+  95\% confidence intervals.  When simulating 2 mode models, we determined the
+  state sequence based on random draws weighted by the appropriate row of the
+  probability transition matrix. We drew hops and dwells based on the current
+  state of the system. Since we calculated the transition probabilities from a
+  finite data set, they have an associated uncertainty which we 
   %MRS4: not quite sure what you mean by incorporating uncertainty. 
@@
   mechanisms in the pore and out of the pore (see Table~\ref{table:states}). We use
-  the same radial cut-off (0.75 nm) as in the anomalous diffusion model to differentiate
+  the same radial cut-off (0.75 nm) as in the AD model to differentiate
   the pore and tail region. These state choices assume that there are no significant
@@
   Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} (also trying it out in 
-  Figures~\ref{fig:radars} and~\ref{fig:radars_nolines})
+  Figures~\ref{fig:radars},~\ref{fig:radars_nolines},~\ref{fig:1mode_bar_charts}, and~\ref{fig:2mode_bar_charts})
 
@@
   % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0.
+  %BJC4: will likely move these tables to supporting.
   \begin{table}[h]
@@
 
+  %BJC4: I think these next two figures are the way to go.
   \begin{figure}
@@
   \end{subfigure}
-  \caption{MSDs generated from realizations of our 1 mode anomalous diffusion models
+  \caption{MSDs generated from realizations of our 1 mode AD models
   agree well with MD-generated data when using an exponential cutoff (sFBMcut and SFLMcut).
@@
   \end{subfigure}
-  \caption{MSDs generated from realization of our 2-mode anomalous diffusion model
+  \caption{MSDs generated from realization of our 2-mode AD model
   also match well to MD-generated data. The MSD of urea appears to be underpredicted
@@
 
-  Truncating the power laws with an exponential cut-off has the largest effect on the on 
-  the match between the MD-calculated MSD and that measured from the simulated anomalous
-  diffusion trajectories. Without truncation, the MD MSDs are underestimated in all cases.
-  This is because dwell times on the order of the MD simulation length are sampled and 
-  incorporated into the simulated anomalous diffusion trajectories, reducing the MSD. 
-  The longest observed dwell time among the solutes was 1.3 $\mu$s by ethylene glycol.
+  Truncating the power laws with an exponential cut-off has the largest effect
+  on the match between the MD-calculated MSD and that measured from the
+  simulated AD trajectories. Without truncation, the MD MSDs are underestimated
+  in all cases. This is because dwell times on the order of the MD simulation
+  length are sampled and incorporated into the simulated anomalous diffusion
+  trajectories, reducing the MSD. The longest observed dwell time among the
+  solutes was 1.3 $\mu$s by ethylene glycol.
 
@@
   a near Gaussian distribution.
-  % BJC4: need to explain this somehow.
 
@@
                            & First Half       & Second Half      \\\hline
-  Urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
+  Urea                     & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
   Ethylene Glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
   Methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
-  Acetic Acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
+  Acetic Acid              & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
 
@@
 
+  %BJC4: This paragraph could use some figures in Supporting
   The non-stationary behavior of ethylene glycol and methanol present themselves
@@
   deviation of the emission distributions from Gaussian behavior is far more pronounced
-  than that seen in the hop length distributions of the previous section, therefore we 
+  than that seen in the hop length distributions of the AD model, therefore we 
   did not consider the Gaussian case (see Figure~\ref{fig:gaussian_levy_comparison}).
@@
   The parameters of the L\'evy stable distributions along with their Hurst parameters 
-  are tabulated in Table~\ref{table:msddm_params}.
+  are tabulated in Table~\ref{table:msddm_params} (and graphically in Figure~\ref{fig:msddm_parameters})
 
@@
 
+  %BJC4: will be replaced with bar charts and moved to SI
   \begin{table}[h]
@@
   %BJC4: better visualization scheme
+  %BJC4: maybe color code background based on whether its in the pore or tails
+  % and then make some kind of code for trapping mechanisms. t - tails, p -
+  % pores, a - associated, h - hbonded. Replace state numbers with codes). For
+  % example, state 4 would be t-a-h
   \begin{figure}
@@
   \begin{subfigure}{0.49\textwidth}
+  %BJC4: add Brownian limit to this? 
   \includegraphics[width=\textwidth]{H_v_state.pdf}
   \caption{}\label{fig:H_v_state}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
+  \caption{}\label{fig:sigma_v_state}
   \end{subfigure}
@@
   \end{subfigure}
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
-  \caption{}\label{fig:sigma_v_state}
-  \end{subfigure}
+  %BJC4: I combined the following bar chart with the parameters. Let me know if that makes things less coherent.
   \begin{subfigure}{0.49\textwidth}
@@
   \end{subfigure}
-  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
-  trajectories and used them to generate realizations of our MSDDM model. The states
-  are defined in Table~\ref{table:states} except state T which describes the transition
-  emissions.}\label{fig:msddm_parameters}
+	  \caption{The parameters of the MSDDM are strong functions of the
+	  trapping mechanisms. We observe differnt parameters but with similar
+	  trends between the tail and pore region. (a) Motion is highly
+	  anti-correlated in trapped states. As the number of simulataneously
+	  influencing trapping mechanisms increases, the hurst parameter
+	  decreases. The hurst parameter is highest during transitions between
+	  states (state T). (b) As more trapping mechanism simultaneously
+	  influence solutes, the width of the hop length distribution
+	  decreases. The largest hops occur when solutes are unbound in the
+	  pores. (c) The weight of the hop length distribution's tails,
+	  parameterized by $\alpha_h$ increases as more trapping mechanism
+	  influence solutes simultaenously. The transition hop distributions
+	  have some of the heaviest tails. (d) Solutes spend varying amounts of
+	  time under the influence of each trapping mechanism. There is less
+	  confidence in the parameters of states that are visited infrequently.
+	  }\label{fig:msddm_parameters}
   \end{figure}
@@
   anti-correlated as indicated by their consistently low Hurst parameters.
-  Perfectly anti-correlated motion ($H$=0) results in no contribution to the solute's
-  MSD. Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
-  trapping mechanisms. Highly anti-correlated behavior in the pores in the absence of
-  any trapping mechanism is likely caused by collisions with monomer head groups 
-  within the pore region. The Hurst parameters for transitional (T) emissions are 2-18 times higher 
-  than emissions from trapped states. The value of $\alpha_h$ for transition 
-  emissions is also relatively low giving higher probabilities to larger hops.
-
-  As solutes are influenced by more trapping effects simultaneously, the width of
-  the hop length distribution, $\sigma$, decreases while its L\'evy index increases.
-  Treating the tail and pore regions independently, $\sigma$ is largest and $\alpha_h$
-  is smallest when solutes are not hydrogen bonding or associating with sodium (states 1 and 5).
-  Solutes are free to move and take occasionally large hops. The smallest $\sigma$
-  and highest $\alpha_h$ values are measured when solutes are hydrogen bonding and 
-  associating with sodium at the same time (states 4 and 8). Motion is restricted 
-  by multiple tethers which maintains a relatively narrow distribution of hop lengths.
-
-  The trapping mechanisms affect each solute to varying degrees. The probabilities
-  of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
-  Urea and acetic acid spend slightly more than half their time in the tails (56\% and 62\% 
-  of their time respectively) while ethylene glycol spends about 44\% of its time in the tails.
-  Urea and acetic acid's compact and flat structure allows it to more easily 
-  partition into the tails while ethylene glycol prefers the pore region due to 
-  its two hydrophilic hydroxyl groups. Meanwhile methanol spends 91 \% of its 
-  time in the tails likely due to its small size.
+  There is a weak negative trend in the Hurst parameters values as the number
+  of simulaneously influencing trapping mechanisms increases
+  (Figure~\ref{fig:H_v_state.pdf}). Perfectly anti-correlated motion ($H$=0)
+  results in no contribution to the solute's MSD. Surprisingly, state 5 $H$
+  values are low despite the solutes being subject to no trapping mechanisms.
+  Highly anti-correlated behavior in the pores in the absence of any trapping
+  mechanism is likely caused by collisions with monomer head groups within the
+  pore region. The Hurst parameters for transitional (T) emissions are 2-18
+  times higher than emissions from trapped states. The value of $\alpha_h$ for
+  transition emissions is also relatively low giving higher probabilities to
+  larger hops.
+
+  As solutes are influenced by more trapping effects simultaneously, the width
+  of the hop length distribution, $\sigma$, decreases while its L\'evy index
+  , $\alpha$, increases (Figures~\ref{fig:sigma_v_state} and~\ref{fig:alpha_v_state}
+  respectively). Treating the tail and pore regions independently, $\sigma$ is
+  largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding or
+  associating with sodium (states 1 and 5). Solutes are free to move and take
+  occasionally large hops. The smallest $\sigma$ and highest $\alpha_h$ values
+  are measured when solutes are hydrogen bonding and associating with sodium at
+  the same time (states 4 and 8). Motion is restricted by multiple tethers
+  which maintains a relatively narrow distribution of hop lengths.
+
+  The trapping mechanisms affect each solute to varying degrees. The
+  probabilities of occupying a given state at any time are plotted in
+  Figure~\ref{fig:state_probabilities}. Urea and acetic acid spend slightly
+  more than half of their time in the tails (56\% and 62\% of their time
+  respectively) while ethylene glycol spends about 44\% of its time in the
+  tails. Urea and acetic acid's compact and flat structure allows it to more
+  easily partition into the tails while ethylene glycol prefers the pore region
+  due to its two hydrophilic hydroxyl groups. Meanwhile methanol spends 91 \%
+  of its time in the tails likely due to its small size.
 
   %MRS4: make it more clear you are still taking about trapping mechanisms here.
-  Urea spends the largest fraction of its time trapped via association with sodium ions.
-  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
-  total time while in the pores (state 7). The electron-dense and unshielded oxygen
-  atom of urea's carbonyl group is prone to associate with positively charged sodium
-  ions. The nitrogen atoms of urea are only weak hydrogen bond donors.
+  Urea spends the largest fraction of its time trapped via association with
+  sodium ions. It does so 31\% of the total time while in the tails (state 3)
+  and 21\% of the total time while in the pores (state 7). The electron-dense
+  and unshielded oxygen atom of urea's carbonyl group is prone to associate
+  with positively charged sodium ions. The nitrogen atoms of urea are only weak
+  hydrogen bond donors.
 
@@
   Methanol spends most of its time unbound in the tail region (state 1) and spends a 
-  significant portion of time hydrogen bonded to while in the tail regions.
+  significant portion of time hydrogen bonding while in the tail regions.
   Most of the tail region hydrogen bonds are donated from methanol to the ether
@@
 
-  Finally, acetic acid spends the majority of it's time hydrogen bonding in and out
-  of the pore.
+  Finally, acetic acid spends the majority of it's time hydrogen bonding in and
+  out of the pore (states 2 and 6). Although it has an unshielded carbonyl group in its
+  structure, association with sodium ions in this environment is apparently a much
+  weaker interaction than hydrogen bonding.
 
@@
   \includegraphics[width=\textwidth]{URE_msddm.pdf}
-  \caption{}\label{fig:URE_msddm}
+  \caption{Urea}\label{fig:URE_msddm}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{GCL_msddm.pdf}
-  \caption{}\label{fig:GCL_msddm}
+  \caption{Ethylene Glycol}\label{fig:GCL_msddm}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{MET_msddm.pdf}
-  \caption{}\label{fig:MET_msddm}
+  \caption{Methanol}\label{fig:MET_msddm}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{ACH_msddm.pdf}
-  \caption{}\label{fig:ACH_msddm}
+  \caption{Acetic Acid}\label{fig:ACH_msddm}
   \end{subfigure}
@@
 
-  %BJC3: would take ~ 20 hours to simulation 10000 trajectories.
   %MRS4: state how much it overestimated (1% or 10000%?)
   %BJC4: added percentages. Is it redundant since I already said how many time
-  The MSDDM over-estimates solute MSDs by 200--300 \% (see Figure~\ref{fig:msddm_performance}). 
-  We simulated 1000 trajectories as described in Section~\ref{method:MSMs} then
-  %BJC3: 2.2 and 3.3 x higher than MD to be exact
-  calculated their MSDs. The MSDs of urea and ethylene glycol are about 2 and 3 times
-  higher than MD simulations respectively.
+  The MSDDM over-estimates solute MSDs by c.a. 300--600 \%. To create
+  Figure~\ref{fig:msddm_performance}, we simulated 1000 trajectories as
+  described in Section~\ref{method:MSMs}, calculated their MSDs and compared
+  them to MD simulated MSD curves. It is clear that the predictive abilities of
+  the MSDDM are inadequate but it is still possible to salvage key insights.
+  %The predicted MSDs of urea and ethylene glycol are about 2 and 3 times
+  %higher than MD simulations respectively.
 
@@
   %BJC4: modified thesis
-  The MSDDM overestimates solute MSDs because correlation is lost
-  every time a state switch occurs. Although correlation exists within each
-  sequence, there is no memory of the previous state or state transition 
-  that can be built into the first emission of the most recent state. 
-  This implies that the first value in a state sequence is a random
-  draw from the underlying emission distribution. Frequent transitions
-  between states lead to an abundance of short dwell times. It is 
-  difficult to accurately correlate short sequences so we are 
-  almost simulating uncorrelated draws from the emission distribution.
-  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying 
-  the transition matrix and simulating a simple 2-state model with parameters
-  similar to those in Table~\ref{table:msddm_params} (see Table~\ref{S-table:msddm_params}
-  of the Supporting Information). We modified the probability
-  transition matrix, $T$, in order to control the probability of 
-  self-transitions (the diagonal elements of $T$). Larger self-transition probabilities lead to longer dwell 
-  times in each state. We set the off-diagonal elements of $T$ to be equal values that make the
-  rows of $T$ sum to unity when combined with the self-transition probabilities. 
-  As we increase the self-transition probability, $T_{ii}$, the simulated MSD 
-  decreases. Consequently longer dwell times in each state allow us to more accurately
-  simulate the negative correlation that we observe in MD.
+  The MSDDM overestimates solute MSDs because correlation is lost every time a
+  state switch occurs. Although correlation exists within each sequence, there
+  is no memory of the previous state or state transition that can be built into
+  the first emission of the most recent state.  This implies that the first
+  value in a state sequence is a random draw from the underlying emission
+  distribution. Frequent transitions between states lead to an abundance of
+  short dwell times. It is difficult to accurately correlate short sequences so
+  we are almost simulating uncorrelated draws from the emission distribution.
+  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying the
+  transition matrix and simulating a simple 2-state model with parameters
+  similar to those in Table~\ref{table:msddm_params} (see
+  Table~\ref{S-table:msddm_params} of the Supporting Information). We modified
+  the probability transition matrix, $T$, in order to control the probability
+  of self-transitions (the diagonal elements of $T$). Larger self-transition
+  probabilities lead to longer dwell times in each state. We set the
+  off-diagonal elements of $T$ to be equal values that make the rows of $T$ sum
+  to unity when combined with the self-transition probabilities.  As we
+  increase the self-transition probability, $T_{ii}$, the simulated MSD
+  decreases. Consequently longer dwell times in each state allow us to more
+  accurately simulate the negative correlation that we observe in MD.
 
@@
   growth exponents. (c) Solutes that spend a large fraction of their time in the tails tend
-  to have larger Hurst parameters.}\label{fig:mfpt_curves}
+  to have lower Hurst parameters.}\label{fig:mfpt_curves}
   \end{figure}
@@
   motion in an H\textsubscript{II} phase LLC membrane. The values obtained for
-  the parameters when fitting the models to the time series data offer important
-  mechanistic insight on the molecular details of transport.
+  the parameters when fitting the models to the time series data offer
+  important mechanistic insight on the molecular details of transport.
   Subordinated fractional Brownian and L\'evy motion have a nice theoretical
   foundation in the anomalous diffusion literature. Our single mode model
-  quantifies and allows comparison of the hopping and trapping behavior 
-  between solutes. A two mode model that describes dynamics based on whether
-  a solute is in or out of the pore region allows us to break down individual
-  solute motion into the two distinct regimes and we showed that solute motion is
-  clearly restricted while in the tail region. Our Markov state-dependent dynamical
-  model uses explicitly defined trapping mechanisms and gives a nice description 
-  of transitions between these observed states, the equilibrium distribution of 
-  solutes among states as well as the type of stochastic behavior shown in each 
-  state. However, it doesn't accurately portray correlated time series behavior
-  leading to overpredicted MSDs.
-
-  %MRS4: test/train in order to show power?
-  We believe that our models have moderate predictive power. 
-  %MRS4: be more precise on how superior is quantified below.
-  The anomalous
-  diffusion model has superior performance to the MSDDM. Both 1 and 2 mode 
-  sFBM and sFLM with truncated power law distributions predict MSDs close 
-  to those simulated with MD while the MSDDM significantly over-predicts MSDs.
-  One might have more success using the MSDDM with a system that exhibits
+  quantifies and allows comparison of the hopping and trapping behavior between
+  solutes. A two mode model that describes dynamics based on whether a solute
+  is in or out of the pore region allows us to break down individual solute
+  motion into two distinct regimes which allowed us to show that solute motion
+  is clearly restricted while in the tail region. Our Markov state-dependent
+  dynamical model uses explicitly defined trapping mechanisms and gives a nice
+  description of transitions between these observed states, the equilibrium
+  distribution of solutes among states as well as the type of stochastic
+  behavior shown in each state. However, it doesn't accurately portray
+  correlated time series behavior leading to overpredicted MSDs.
+
+  We believe that our models have moderate predictive power. The AD model has
+  superior predicitive performance to the MSDDM. Both 1 and 2 mode sFBM and
+  sFLM with truncated power law distributions predict MSDs close to those
+  simulated with MD while the MSDDM significantly over-predicts MSDs. One
+  might have more success using the MSDDM with a system that exhibits
   infrequent transitions between states.
 
-  Our mathematical models help us think about how to design LLC monomers for 
+  Both mathematical models help us think about how to design LLC monomers for
   solute-specific separations by forcing us to think in terms of controlling
-  solute trapping. The anomalous diffusion model is quite flexible because it
-  does not require knowledge of specific trapping mechanisms. Screening a set
-  of solutes and applying the anomalous diffusion model can help uncover
-  trapping mechanisms by forcing the scientist to identify features common 
-  to solutes with long or short hop lengths and dwell times. The MSDDM is a 
-  powerful way to characterize explicit trapping mechanisms. Although its
-  predictive power is inferior to the anomalous diffusion model, it clearly
-  partitions a trajectory into discrete mechanisms and quantifies their
-  relative dominance in the real system. For example, it is clear that 
-  sodium ion association is primarily responsible for trapping urea while 
-  hydrogen bonding dominates ethylene glycol. If one re-designs an LLC monomer
-  to eliminate one source of trapping, 
-  %MRS4: by what mechanisms are high selectivities possible?
-  then high selectivities are possible.
+  solute trapping. The AD model is quite flexible because it does not require
+  knowledge of specific trapping mechanisms. Screening a set of solutes and
+  applying the anomalous diffusion model can help uncover trapping mechanisms
+  by forcing the scientist to identify features common to solutes with long or
+  short hop lengths and dwell times. The MSDDM is a powerful way to
+  characterize explicit trapping mechanisms. Although its predictive power is
+  inferior to the AD model, it clearly partitions a trajectory
+  into discrete mechanisms and quantifies their relative dominance in the real
+  system. For example, it is clear that sodium ion association is primarily
+  responsible for trapping urea while hydrogen bonding dominates ethylene
+  glycol. If one re-designs an LLC monomer to eliminate one source of trapping,
+  then high selectivities may be possible.
+
+  Finally, using our most promising predictive model, we showed how one can understand
+  the relationship between MFPT and pore length. One cannot avoid an at least 
+  length-squared dependence, however this relationship is exacerbated by the
+  degree of anti-corrlation a solute faces. Designing monomers to keep solutes
+  out of the tails where anti-correlated behavior dominates may lead to 
+  significant advances in LLC membrane permeability.
 

### 2019-11-26 Ben_Manuscripts/stochastic_transport/Draft.tex
Updated figure designs to help readers

@@
 	  \caption{The parameters of the MSDDM are strong functions of the
-	  trapping mechanisms. We observe differnt parameters but with similar
-	  trends between the tail and pore region. (a) Motion is highly
-	  anti-correlated in trapped states. As the number of simulataneously
-	  influencing trapping mechanisms increases, the hurst parameter
-	  decreases. The hurst parameter is highest during transitions between
-	  states (state T). (b) As more trapping mechanism simultaneously
-	  influence solutes, the width of the hop length distribution
-	  decreases. The largest hops occur when solutes are unbound in the
-	  pores. (c) The weight of the hop length distribution's tails,
-	  parameterized by $\alpha_h$ increases as more trapping mechanism
-	  influence solutes simultaenously. The transition hop distributions
-	  have some of the heaviest tails. (d) Solutes spend varying amounts of
-	  time under the influence of each trapping mechanism. There is less
-	  confidence in the parameters of states that are visited infrequently.
+	  trapping mechanisms. We observe different parameters but with similar
+	  trends between the tail and pore region. The states are defined in
+	  Table~\ref{table:states}. To aid the reader, we labeled each state
+	  with an abbreviation which identifies the combination of conditions
+	  to which each solute is subject: t - tails, p - pores, h - hydrogen
+	  bonded, a - associated with sodium. The legend in (a) applies to all
+	  subplots. (a) Motion is highly anti-correlated in trapped states. As
+	  the number of simulataneously influencing trapping mechanisms
+	  increases, the hurst parameter decreases. The hurst parameter is
+	  highest during transitions between states (state T). (b) As more
+	  trapping mechanism simultaneously influence solutes, the width of the
+	  hop length distribution decreases. The largest hops occur when
+	  solutes are unbound in the pores. (c) The weight of the hop length
+	  distribution's tails, parameterized by $\alpha_h$ increases as more
+	  trapping mechanism influence solutes simultaenously. The transition
+	  hop distributions have some of the heaviest tails. (d) Solutes spend
+	  varying amounts of time under the influence of each trapping
+	  mechanism. There is less confidence in the parameters of states that
+	  are visited infrequently.
 	  }\label{fig:msddm_parameters}

### 2019-12-03 Ben_Manuscripts/stochastic_transport/Draft.tex
New ways to fit FPT distribution

--- 2019-11-26 Ben_Manuscripts/stochastic_transport/Draft.tex
@@
   macroscopic properties. We use two different stochastic time series models,
-  parameterized from long molecular dynamics (MD) simulation trajectories, in order
-  to predict solute mean squared displacements (MSDs). With our first model, based
-  on the anomalous diffusion literature, we show how solute dynamics can be modeled as
-  a fractional diffusion process subordinate to a continuous time random walk.
-  We parameterize the distribution of dwell times, hop lengths between dwells and
-  correlation between hops. We explore 2 variations of the model. The first variation
-  applies a single set of parameters to the solutes and the second applies 2 sets
-  of parameters based on the solute's radial distance from the closest pore center.
-  Our second model, an adaptation of Markov state models, treats the configurational
+  parameterized from long molecular dynamics (MD) simulation trajectories, in
+  order to predict solute mean squared displacements (MSDs) and mean first 
+  passage times (MFPTs) in macroscopic length pores. With our first model, 
+  based on the anomalous diffusion theory, we show how solute dynamics can be
+  modeled as a fractional diffusion process subordinate to a continuous time 
+  random walk. From the MD simulations, we parameterize the distribution of 
+  dwell times, hop lengths between dwells and correlation between hops. We 
+  explore 2 variations of the anomalous diffusion model. The first variation
+  applies a single set of parameters to the solute displacements and the second
+  applies 2 sets of parameters based on the solute's radial distance from the closest pore center.
+  Our second model, a generalization of Markov state models, treats the configurational
   state of the system as a Markov process, each of which has state dependent 
-  transport behavior. For each state and transition between states, we parameterized
+  transport behavior. For each state and transition between states, we parameterize
   the distribution and temporal correlation structure of positional fluctuations as
@@
   simulations. The anomalous diffusion model shows superior predictive performance, 
-  in many cases reproducing MD results well within error. Finally, we use the 
-  parameters of each model to identify specific differences in solute transport
-  behavior which can help suggest modifications that can be made to LLC membrane 
-  monomers in order to increase or reduce selectivity towards a specific solute
-  or class of solutes.
+  in many cases reproducing MD results well within error. Finally, we demonstrate 
+  how one can use our models in order to calculate mean first passage time, and 
+  therefore solute flux, of a given solute across a macroscopic-length pore. Overall,
+  this works helps connect the relationship between microscopic chemically-dependent
+  solute motions and macroscopic membrane performance.
+
+%  Finally, we use the 
+%  parameters of each model to identify specific differences in solute transport
+%  behavior which can help suggest modifications that can be made to LLC membrane 
+%  monomers in order to increase or reduce selectivity towards a specific solute
+%  or class of solutes.
 
@@
   value is more representative of a typical passage time rather than a mean.
+
+  \begin{equation}
+  F(t) = erfc\bigg(\frac{x - vt}{2\sqrt{D t}}\bigg)
+  \end{equation}
 
@@
   %BJC4: another way to visualize data
-  %BJC4: I think these are kind of hard to read. Can't really see any trends.
+  %BJC4: I think these are kind of hard to read. Can't really see any trends. Open to other
+  %ideas.
   \begin{figure}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{2mode_radar_nolines.eps}   % for some reason it has trouble saving this as a PDF (.eps doesn't show opacity)
+  \includegraphics[width=\linewidth]{2mode_radar_nolines.png}   % for some reason it has trouble saving this as a PDF
   \caption{}\label{fig:2mode_radar}
@@
 %  \end{figure}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
-  \caption{$\mathcal{N}(\sigma) / L(\sigma, \alpha_h)$}\label{fig:1mode_AD_hops}
-  \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
-  \caption{$P(\alpha_d) / P_T(\alpha_d, \lambda)$}\label{fig:1mode_AD_dwells}
-  \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
-  \caption{$\gamma(H)$}\label{fig:hurst_barchart}
-  \end{subfigure}
-  \caption{The parameters of the 1 mode model reveal differences in solute
-	  dynamics. (a) We parameterized Gaussian ($\mathcal{N}(\sigma)$,
-	  parameters given by bars with white background) and L\'evy stable
-	  ($L(\sigma, \alpha_h)$, parameters given by bars with gray
-	  background) distributions to describe solute hop lengths. We assume
-	  the mean ($\mu$) to be zero for these distributions and there to be
-	  no skewness ($\beta=0$) in the L\'evy stable distributions. High
-	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
-	  hops. (b) We parameterized a pure power law ($P(\alpha_d)$, white
-	  background) and a truncated power law ($P_T(\alpha_d, \lambda)$, gray
-	  background) distribution to describe solute dwell times. Lower values
-	  of $\alpha_d$ lead to heavier power law tails and higher values of
-	  $\lambda$ truncate the distribution at lower dwell times.(c) Finally,
-	  we parameterized the hop autocorrelation function ($\gamma(H)$) to
-	  describe the degree of correlation between hops.  Higher values of
-	  $H$ display closer to Brownian behavior.
-	  }\label{fig:1mode_bar_charts}
-  \end{figure}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_AD_hops.pdf}
-  \caption{$\mathcal{N}(\sigma) / L(\sigma, \alpha_h)$}\label{fig:2mode_AD_hops}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
-  \caption{$P(\alpha_d) / P_T(\alpha_d, \lambda)$}\label{fig:2mode_AD_dwells}
-  \end{subfigure}
-  \caption{The two mode model parameterizes solute behavior in the pores and
-	  tails separately. Mode 1 corresponds to solute behavior within 0.75
-	  nm of the pore center, the pore region, and mode 2 corresponds to
-	  behavior greater than or equal to 0.75 nm from the pore center, the
-	  tail region. (a) Generally, movement is much more restricted in the
-	  tail region shown by lower mode 2 $\sigma$ values for the Normal
-	  (white background) and L\'evy distributions (gray background). Values
-	  of $\alpha$ are significantly lower for urea and acetic acid meaning
-	  there is a larger probability that they will take large hops.
-	  (b) Dwell times are longer in in the tails. Lower values of
-	  $\alpha_d$ correspond to power laws with heavier tails and thus
-	  higher probabilities of long dwell times. There is no easily
-	  discernable trend in $\lambda$ of the truncated power law
-	  distribution (gray background).  Note that we used the same Hurst
-	  parameter for both modes due to a low number of sufficiently long
-	  sequences of hops in each mode. See Figure~\ref{fig:1mode_bar_charts}
-	  for descriptions of the parameters.
-  }\label{fig:2mode_bar_charts}
-  \end{figure}
 

### 2019-12-03 LLC_Membranes/timeseries/mfpt_pore.py

@@ -3,19 +3,17 @@
 """ Find the mean first passage time (MFPT) of a type of particle
 """
 
-from LLC_Membranes.llclib import timeseries, file_rw, rand, stats
+from LLC_Membranes.llclib import timeseries, file_rw, rand, stats, fitting_functions
 from LLC_Membranes.timeseries.fractional_levy_motion import FLM
 from LLC_Membranes.timeseries import flm_sim_params
 from LLC_Membranes.analysis.sfbm_parameters import SFBMParameters
+from scipy.integrate import quad
+from scipy.optimize import curve_fit
 import matplotlib.pyplot as plt
-from matplotlib import animation
 import numpy as np
 import tqdm
 from multiprocessing import Pool
-from scipy.sparse import csr_matrix as sparse_matrix
 import warnings
-from scipy.stats import norm
-import levy
 import fbm
 import yaml
 import argparse
@@ -68,10 +66,10 @@ class Hops:
             print('Generating corrections to truncated Levy stable distribution...', end='', flush=True)
             self.hurst_correction = flm_sim_params.HurstCorrection()
             self.truncation_correction = flm_sim_params.TruncateLevy()
-            corrected_max_hop = self.truncation_correction.interpolate(self.params[2], self.params[1] - .01,
-                                                                       self.params[3], self.params[0])
-            self.flm = FLM(self.hurst_correction.interpolate(self.params[2], self.params[1]), self.params[1],
-                           scale=self.params[0],
+            corrected_max_hop = self.truncation_correction.interpolate(self.params[0], self.params[1] - .01,
+                                                                       self.params[2], self.params[3])
+            self.flm = FLM(self.hurst_correction.interpolate(self.params[0], self.params[1]), self.params[1],
+                           scale=self.params[3],
                            N=self.length, M=4, correct_hurst=False, truncate=corrected_max_hop, correct_truncation=False)
             print('Done!')
 
@@ -186,7 +184,7 @@ class Dwell:
 class MeanFirstPassageTime:
 
     def __init__(self, L, n, nT, pickled_parameters=None, hop_params=None, dwell_params=None, dt=1., nbins=25,
-                 nt=1, save=True, concentration_profile=False):
+                 nt=1, save=True, concentration_profile=False, load_passage_times=None):
         """ Generate trajectories from which to calculate mean first passage times. One can also use them to calculate
         the concentration profile within the pore
 
[…]

### 2019-12-04 Ben_Manuscripts/stochastic_transport/Draft.tex
Added databases for levy corrections

@@
 
-  \subsection{Mean First Passage Time}\label{method:mfpt}
-
-  We used the mean first passage time (MFPT) in order to quantify how long it would take a 
-  typical particle, parameterized with the above models, to travel across a membrane pore
-  of length $L$. To measure this quantity, we simulated 50000 realizations of particle 
-  trajectories, released at the pore entrance ($z=0$). In the case of uncorrelated hops, one
-  can continuously draw from the hop length distribution until $z \geq L$ (or $-L$ for 
-  the sake of computational efficiency). The length of time between the last time the 
-  particle crossed $z=0$ and the end of the trajectory gives a single passage time. 
-  When particle hops are correlated, as they are in all cases of this work, we cannot 
-  continuously construct the particle trajectories. Rather, we must generate trajectories
-  of length $n$ and measure the length of the sub-trajectory which traverses from $0$ 
-  to $L$ without becoming negative.
+  \subsection{Solute Flux}\label{method:mfpt}
+
+  We determined the rate at which solutes cross macroscopic-length pores based on the
+  Hill relation:~\cite{hill_free_1989}
+  \begin{equation}
+  J = \frac{1}{MFPT}
+  \end{equation}
+  where $J$ is solute flux and MFPT refers to the mean first passage time. In the 
+  context of our work, the MFPT describes the average length of time it takes a particle
+  to move from the pore entrance to the pore exit.
+
+  We generated particle trajectories, parameterized with the above models, in order
+  to construct a distribution of first passage times across a membrane pore of length $L$.
+  We simulated 50000 trajectory realizations, released at the pore entrance ($z=0$). In the case of 
+  uncorrelated hops, one can continuously draw from the hop length distribution until 
+  $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
+  between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
+  single passage time. When particle hops are correlated, as they are in all cases of
+  this work, we cannot continuously construct the particle trajectories. Rather, we must
+  generate trajectories of length $n$ and measure the length of the sub-trajectory 
+  which traverses from $0$ to $L$ without becoming negative.
   %BJC4: below is only necessary if you the mean of the distribution exists.
@@
 
-  Our definition of the MFPT differs from more standard treatments. The setup of our 
-  system is consistent with a one dimensional interval with two absorbing boundaries. In
-  the absence of an external force and with a constant diffusion coefficient,
-  $D$, the MFPT is simply:
+  We calculated the expected value of analytical fits to the passage time distributions
+  in order to determine the MFPT for a given solute and pore length. One should not 
+  use the mean of the empirical passage time distribution because it is highly likely
+  that the true MFPT will be underestimated unless 100\% of a very large number of 
+  trajectories reach $L$. If a trajectory does not reach $L$ within $n$ steps, it is
+  possible that a very long passage time has been excluded from the distribution.
+
+  %BJC4: can probably delete this paragraph
+%  We are unaware of an analytical passage time distribution which describes our 
+%  geometry. The setup of our system is consistent with a one dimensional interval 
+%  with two absorbing boundaries. In the absence of an external force and with a constant
+%  diffusion coefficient, $D$, the MFPT is simply:
+%  \begin{equation}
+%  T = \frac{z_0(L - z_0)}{2D}
+%  \end{equation}
+%  where $z_0$ is the initial position of particle trajectories.~\cite{gitterman_mean_2000}
+%  Of course that implies a conventional MFPT of 0 since particles overwhelmingly exit the
+%  pore at $z=0$. Therefore, we chose only to include trajectories in the MFPT calculation 
+%  which cross the boundary at $L$. We are unaware of an analytical form of the MFPT or 
+%  the distribution of passage times describing our system even in the simplest case of 
+%  Brownian increments. %BJC4: still digging for an analytical solution. Rich said the 
+%  %'marathon' runner problem might give a solution. It may be the same as the distribution
+%  % of runners crossing the finish line
+
+  To come up with an analytical equation describing the passage time distributions, 
+  one can frame the problem as a pulse of particles at the pore inlet ($z=0$) that 
+  spreads out over time as it approaches $L$.
+
+%  This pulse model effectively describes
+%  the time-dependent probability distribution of particles which eventually reaches 
+%  $L$. The diffusion equation describing this situation is:
+%  \begin{equation}
+%  \frac{\partial c}{\partial t} + v\frac{\partial c}{\partial x} = D\frac{\partial^2 c}{\partial x^2}
+%  \end{equation}
+%  where $v$ is some average velocity describing the location of the center of the
+%  distribution and $D$ is a diffusion constant. 
+%  One can show that the normalized
+%  concentration profile is:
+  First, consider a pulse spreading out with a fixed mean. It is well known that the 
+  time-dependent probability distribution of particle positions is:
   \begin{equation}
-  T = \frac{z_0(L - z_0)}{2D}
+  p(x, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-x^2}{4Dt}\bigg)
   \end{equation}
-  where $z_0$ is the initial position of particle trajectories.~\cite{gitterman_mean_2000}
-  Of course that implies a conventional MFPT of 0 since particles overwhelmingly exit the
-  pore at $z=0$. Therefore, we chose only to include trajectories in the MFPT calculation 
-  which cross the boundary at $L$. We are unaware of an analytical form of the MFPT or 
-  the distribution of passage times describing our system even in the simplest case of 
-  Brownian increments. %BJC4: still digging for an analytical solution. Rich said the 
-  %'marathon' runner problem might give a solution. It may be the same as the distribution
-  % of runners crossing the finish line
-
-  %BJC4: I'm not sure the best way to get the peak
-  In the absence of an analytical equation for the MFPT, we instead report the location of
-  the peak of the passage time distribution. This has the added advantage of treating
-  cases where the passage time distribution diverges and no mean exists. While we will
-  call the peak in the distribution the MFPT, it is important to recognize that this 
-  value is more representative of a typical passage time rather than a mean.
-
+  We can make the substitution $x = x - vt$ in order to linearly shift the mean as a
+  function of time:
   \begin{equation}
-  F(t) = erfc\bigg(\frac{x - vt}{2\sqrt{D t}}\bigg)
+  p(x, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-(x - vt)^2}{4Dt}\bigg)
   \end{equation}
+  One can track the number of the fraction of particles, $F$, that have crossed the pore 
+  boundary by integrating:
+  \begin{equation}
+  F = \int_x^\infty p~ dx = erfc\bigg(\frac{x - vt}{2\sqrt{D t}}\bigg)
+  \end{equation}
+  and finally take the derivative to arrive at the first passage time distribution:
+  \begin{equation}
+  P = -\frac{1}{\sqrt{\pi}}e^{-(x - vt)^2 / (4Dt)}\bigg(-\frac{D(x - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
+  \end{equation}
+
+  %BJC4: we have better ways of getting peaks now
+%  In the absence of an analytical equation for the MFPT, we instead report the location of
+%  the peak of the passage time distribution. This has the added advantage of treating
+%  cases where the passage time distribution diverges and no mean exists. While we will
+%  call the peak in the distribution the MFPT, it is important to recognize that this 
+%  value is more representative of a typical passage time rather than a mean.
 

### 2019-12-04 Ben_Manuscripts/stochastic_transport/Draft.tex
removed test from name

@@
   To come up with an analytical equation describing the passage time distributions, 
-  one can frame the problem as a pulse of particles at the pore inlet ($z=0$) that 
-  spreads out over time as it approaches $L$.
-
-%  This pulse model effectively describes
-%  the time-dependent probability distribution of particles which eventually reaches 
-%  $L$. The diffusion equation describing this situation is:
-%  \begin{equation}
-%  \frac{\partial c}{\partial t} + v\frac{\partial c}{\partial x} = D\frac{\partial^2 c}{\partial x^2}
-%  \end{equation}
-%  where $v$ is some average velocity describing the location of the center of the
-%  distribution and $D$ is a diffusion constant. 
-%  One can show that the normalized
-%  concentration profile is:
-  First, consider a pulse spreading out with a fixed mean. It is well known that the 
-  time-dependent probability distribution of particle positions is:
+  one can frame the problem as a pulse of particles instantaneously released at the 
+  pore inlet ($z=0$) which moves at a constant velocity and spreads out as it 
+  approaches $L$. This gives results equivalent to if we had released each particle
+  individually and then analyzed the positions of the ensemble of trajectories as 
+  a function of time.
+
+  First, consider an initial pulse spreading out over time with a fixed mean. We can
+  solve for the time-dependent probability density of particle positions by solving 
+  the one dimensional diffusion equation:
   \begin{equation}
-  p(x, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-x^2}{4Dt}\bigg)
+  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
   \end{equation}
-  We can make the substitution $x = x - vt$ in order to linearly shift the mean as a
+  The appropriate initial and boundary conditions are:
+  \begin{equation}
+  BC1: t > 0, z = \infty, p = 0
+  \end{equation}
+  \begin{equation}
+  BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0
+  \end{equation}
+  \begin{equation}
+  IC: t = 0, c = M\delta(z)
+  \end{equation}
+  where $M$ is the total number of particles in the system. It has been shown 
+  elsewhere that the solution to this equation is:
+  \begin{equation}
+  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-z^2}{4Dt}\bigg)
+  \end{equation}
+  We can make the substitution $z = z - vt$ in order to linearly shift the mean as a
   function of time:
   \begin{equation}
-  p(x, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-(x - vt)^2}{4Dt}\bigg)
+  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
   \end{equation}
-  One can track the number of the fraction of particles, $F$, that have crossed the pore 
+  One can track the fraction of particles, $F$, that have crossed the pore 
   boundary by integrating:
   \begin{equation}
-  F = \int_x^\infty p~ dx = erfc\bigg(\frac{x - vt}{2\sqrt{D t}}\bigg)
+  F = \int_L^\infty p~dz = erfc\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
   \end{equation}
-  and finally take the derivative to arrive at the first passage time distribution:
+  where $L$ is the pore length. This represents the cumulative first passage 
+  time distribution so we take its derivative in order to arrive at the first
+  passage time distribution:
   \begin{equation}
-  P = -\frac{1}{\sqrt{\pi}}e^{-(x - vt)^2 / (4Dt)}\bigg(-\frac{D(x - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
+  P = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
+  \label{eqn:passage_times}
   \end{equation}

### 2019-12-04 LLC_Membranes/llclib/fitting_functions.py

@@ -20,14 +20,29 @@ def continuum_passage_time_distribution(t, x, v, D):
     # This is exact and allows evaluation at single time point
     # a = np.exp(-(x - t * v)**2 / (4 * D * t))  # faster but causes underflow errors
     if type(t) is np.ndarray:
-        a = np.array([float(mpmath.exp(-(x - i * v)**2 / (4 * D * i))) for i in t])  # mpmath has arbitrary precision
+        a = np.array([np.float(mpmath.exp(-(x - i * v)**2 / (4 * D * i))) for i in t])  # mpmath has arbitrary precision
     else:
         a = float(mpmath.exp(-(x - t * v)**2 / (4 * D * t)))
 
     b = D * (x - t * v) / (4 * (D * t) ** 1.5)
     c = v / (2 * np.sqrt(D * t))
 
-    return -(1 / np.sqrt(np.pi)) * a * (-b - c)
+    try:
+        return -(1 / np.sqrt(np.pi)) * a * (-b - c)
+    except FloatingPointError:
+
+        if type(a) is np.ndarray:
+            print(a)
+            A = []
+            for i in a:
+                if i < 1e-300:
+                    A.append(0)
+                else:
+                    A.append(i)
+            print(A)
+            return np.array(A)
+        else:
+            return 0
 
 
 def continuum_ptime_distribution_expected_value(t, x, v, D):

### 2019-12-06 Ben_Manuscripts/stochastic_transport/Draft.tex
New flux curves

@@
   J = \frac{1}{MFPT}
+  \label{eqn:hill_relation}
   \end{equation}
-  where $J$ is solute flux and MFPT refers to the mean first passage time. In the 
-  context of our work, the MFPT describes the average length of time it takes a particle
+  where $J$ is the single particle solute flux and MFPT refers to the mean first passage
+  time. For particle concentrations higher than 1 at the pore entrance, one can multiply
+  Equation~\ref{eqn:hill_relation} by the total number of particles to get the total flux.
+  In the context of our work, the MFPT describes the average length of time it takes a particle
   to move from the pore entrance to the pore exit.
@@
 
-  First, consider an initial pulse spreading out over time with a fixed mean. We can
-  solve for the time-dependent probability density of particle positions by solving 
-  the one dimensional diffusion equation:
+  To derive an analytical equation, first consider an initial pulse spreading out 
+  over time with a fixed mean. We can solve for the time-dependent probability density
+  of particle positions by solving the one dimensional diffusion equation:
   \begin{equation}
@@
   The appropriate initial and boundary conditions are:
-  \begin{equation}
-  BC1: t > 0, z = \infty, p = 0
-  \end{equation}
-  \begin{equation}
-  BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0
-  \end{equation}
-  \begin{equation}
-  IC: t = 0, c = M\delta(z)
-  \end{equation}
+  $$BC1: t > 0, z = \infty, p = 0$$
+  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
+  $$IC: t = 0, c = M\delta(z)$$
   where $M$ is the total number of particles in the system. It has been shown 
-  elsewhere that the solution to this equation is:
+  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
   \begin{equation}
@@
   \end{equation}
-  We can make the substitution $z = z - vt$ in order to linearly shift the mean as a
-  function of time:
+  We can make the substitution $z = z - vt$, where $v$ represents a constant average
+  velocity, in order to linearly shift the mean as a function of time:
   \begin{equation}
@@
   \begin{equation}
-  F = \int_L^\infty p~dz = erfc\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
+  F(t) = \int_L^\infty p~dz = erfc\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
   \end{equation}
@@
   \begin{equation}
-  P = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
+  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
   \label{eqn:passage_times}
   \end{equation} 
+  where the only free parameters for fitting are $v$ and $D$. We calculated the
+  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT.
+
+  We used the ratio of solute fluxes in order to determine membrane selectivity, $S$,
+  towards solutes. Selectivity of solute $i$ versus $j$ is defined in terms of the
+  ratio of solute permeabilities, $P$:~\cite{guo_pervaporation_2004}
+  \begin{equation}
+  S_{ij} = \frac{P_i}{P_j}
+  \end{equation}
+  We can relate this to solute flux using Kedem and Katchalsky's equations for 
+  solvent volumetric flux, $J_v$, and solute flux, $J_s$:~\cite{kedem_permeability_1963}
+  %al-zoubi_rejection_2007 clarifies that these equations can be used for nanofiltration, ultrafiltration etc. by treating the membrane as a black box subject to irreversible thermodynamics.
+  \begin{equation}
+  J_v = L_p(\Delta P - \Delta \pi)
+  \end{equation} 
+  \begin{equation}
+  J_s = P_s \Delta C + (1 - \sigma)CJ_v
+  \label{eqn:solute_flux}
+  \end{equation}
+  where $L_p$ is the pure water permeability, $\Delta P$ and $\Delta \pi$ are the 
+  trans-membrane hydraulic and osmotic pressure differences, $\sigma$ is the reflection
+  coefficient, $P_s$ is the solute permeability, $\Delta C$ is the trans-membrane
+  solute concentration difference and $C$ is the mean solute concentration. Since our
+  simulations do not include convective solute flux, we eliminate the second term 
+  of Equation~\ref{eqn:solute_flux} which allows us to derive a simple expression
+  for selectivity in terms of solute flux:
+  \begin{equation}
+  S_{ij} = \frac{J_i / \Delta C_i}{J_j / \Delta C_j}
+  \label{eqn:selectivity}
+  \end{equation}
+
+%    $$ A_i = \frac{J}{(\Delta P - \Delta \pi)} $$
+%  $$ S = \frac{A_i}{A_j} for a given pore length, L$$
+%  $$J = A(\Delta P - \Delta \pi)$$
+%  $$A = \frac{P_i}{L} $$
+%  $$P_i = \frac{flux}{drivingforce \cdot L} [=] \frac{particles}{s \cdot bar \cdot L}$$
 
@@
 
-  %BJC4: another way to visualize data
-  %BJC4: I think these are kind of hard to read. Can't really see any trends. Open to other
-  %ideas.
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{1mode_radar.pdf}
-  \caption{}\label{fig:1mode_radar}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{2mode_radar.pdf}
-  \caption{}\label{fig:2mode_radar}
-  \end{subfigure}
-  \caption{Another way to visualize Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}}\label{fig:radars}
-  \end{figure}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
-  \caption{}\label{fig:1mode_radar}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\linewidth]{2mode_radar_nolines.png}   % for some reason it has trouble saving this as a PDF
-  \caption{}\label{fig:2mode_radar}
-  \end{subfigure}
-  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
-  \end{figure}
+  %BJC4: another (bad) way to visualize data
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{1mode_radar.pdf}
+%  \caption{}\label{fig:1mode_radar}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{2mode_radar.pdf}
+%  \caption{}\label{fig:2mode_radar}
+%  \end{subfigure}
+%  \caption{Another way to visualize Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}}\label{fig:radars}
+%  \end{figure}
+%  
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
+%  \caption{}\label{fig:1mode_radar}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{2mode_radar_nolines.png}   % for some reason it has trouble saving this as a PDF
+%  \caption{}\label{fig:2mode_radar}
+%  \end{subfigure}
+%  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
+%  \end{figure}
 
@@
 
-  \subsection{Solute Mean First Passage Times}\label{section:mfpt}
+  \subsection{Solute Flux}\label{section:mfpt}
 
@@
   diffusion model in order to demonstrate how one can use its realizations in
-  order to calculate the MFPT (section~\ref{method:mfpt}) of solutes given model 
-  parameters extracted from MD simulations. Any approach which allows one to 
-  generate realizations of solute trajectories can be used in place of the AD model.
-
-  In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
-  with pore length. We fit a curve of the form $cL^{\alpha}$ to the curves in order
-  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
-  to the solute MSDs which is consistent with longer passage times for solutes that
-  progress through the pores more slowly.
-
-  The growth exponent is inversely related to the hurst parameter, $H$. In 
-  Figure~\ref{fig:mfpt_curves_brownian}, we removed the correlation structure (set
-  $H$=0.5) from AD trajectory realizations so that all hops were uncorrelated.
-  Regardless of the parameters of the dwell time distribution, the growth 
-  exponent is always about 2, the same value that we observe for Brownian 
-  motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the Supporting 
-  Information).
-
-  % BJC5: I'm not sure the best way to calculate statistics on this. Since I don't know
-  % the density function of the mean first passage time distribution, I use bins to 
-  % to locate the peaks. So the error bars are dependent on the bin width. 
+  order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
+  parameters extracted from MD simulations. We believe the 1-mode sFBMcut model
+  shows the most promising predictive ability of the models studied in this work. 
+  %Any approach which allows one to 
+  %generate realizations of solute trajectories can be used in place of the AD model.
+
+  %BJC4: not sure if the next couple paragraphs belong in methods
+  It is computationally unfeasible to simulate trajectories long enough that they
+  traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
+  LLC membrane synthesized with the monomer in this work was 7$\mu$m thick. Using
+  24 cores to simulate trajectory realizations in parallel, it takes on the order 
+  of 1 day to simulate 50000 realizations of solutes traversing a 50 nm pore. The 
+  RAM requirements and performance scales greater than linearly and thus would 
+  take an unfeasible amount of memory and time to simulate transport through a 
+  pore over 100 times longer.
+
+  %BJC4: methods?
+  We used simulated trajectories which traverse computationally-reasonable length
+  pores in order to construct an empirical model which one can use to estimate 
+  particle flux for arbitrary length pores. As shown in Figure~\ref{fig:flux_curves},
+  the flux appears to scale according to a power law of the form:
+  \begin{equation}
+  J(L) = cL^{-\beta} 
+  \label{eqn:flux_decay}
+  \end{equation}
+  %while the MFPT scales as its inverse, $(1/c)L^{\beta}$.
+
+  The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
+  solute MSD while the value of the growth exponent, $\beta$, is inversely 
+  related to the Hurst parameter, $H$ (see Figure~\ref{fig:flux_parameters}).
+  In Figure~\ref{fig:flux_curves_brownian}, we removed the correlation 
+  structure (set $H$=0.5) from AD trajectory realizations so that all hops 
+  were uncorrelated. Regardless of the parameters of the dwell time distribution,
+  the growth exponent is always about 2, the same value that we observe for 
+  Brownian motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the 
+  Supporting Information).
+
+  Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
+  highlights that anti-correlation between hops plays a major role in solute flux.
+  With a pore length of 50 nm, the flux of the fasted moving solute, ethylene glycol is 
+  c.a. 5 times lower with versus without anti-correlated hops. The flux of the slowest
+  moving solute, acetic acid, is about 16 times lower by the same comparison. This 
+  difference will only grow with increasing pore length. Note also that the ranking
+  of solute fluxes changes. Methanol jumps from the second lowest to the highest
+  flux when we remove hop correlation. The high degree of anti-correlation among
+  hops made by methanol outweighs its relatively wide hop length distribution.
+
+%   In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
+%  with pore length. We fit a curve of the form  to the curves in order
+%  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
+%  to the solute MSDs which is consistent with longer passage times for solutes that
+%  progress through the pores more slowly.
+
+  %BJC: need simulations with increased length for L=35-50 nm pores of acetic acid and methanol
+  %BJC: see of clauset has better way of fitting t^-alpha (alpha might be too big)
+  %BJC: not sure mfpt is necessary. Takes up space.
+  %BJC: change alpha to beta
+  %BJC: make a chart with parameters
+  %BJC: should have a paragraph about c -- roughly follows their MSDs.
   \begin{figure}
@@
   \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
-  \caption{Correlated Hops}\label{fig:mfpt_curves_regular}
-  \end{subfigure}
+  \includegraphics[width=\textwidth]{flux_curves.pdf}
+  \caption{Fits to $cL^{-\beta}$}\label{fig:flux_curves_regular}
+  \end{subfigure}
+  % BJC: could use better color scheme. Maybe outline hurst parameters
   \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
-  \caption{Uncorrelated Hops}\label{fig:mfpt_curves_brownian}
-  \end{subfigure}
+  \includegraphics[width=\textwidth]{flux_parameters.pdf}
+  \caption{}\label{fig:flux_parameters}
+  \end{subfigure}
+%  \begin{subfigure}{0.475\textwidth}
+%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
+%  \caption{}\label{fig:mfpt_curves}
+%  \end{subfigure}
+  %BJC: going out to 3 decimal places seems silly
+  %BJC: might get closer to beta=2 if I use different curve fitting technique than fitting line to log-log
   \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{frac_pore.pdf}  % This figure might fit in earlier
-  \caption{}\label{fig:frac_pore}
-  \end{subfigure}
-  \caption{(a) We fit the MFPT versus pore length to a function of the form $cL^{\alpha}$. 
-  The MFPT grows super-linearly with increasing pore length. Solutes with lower MSDs have
-  higher MFPTs. (b) If we remove correlation between hops, the MFPTs reduce significantly
-  and the growth exponent stays constant at 2 for all solutes independent of dwell
-  distribution parameters. Higher degrees of anti-correlation (lower $H$) lead to higher
-  growth exponents. (c) Solutes that spend a large fraction of their time in the tails tend
-  to have larger Hurst parameters.}\label{fig:mfpt_curves}
+  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
+  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
+  \end{subfigure}
+%  \begin{subfigure}{0.475\textwidth}
+%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
+%  \caption{}\label{fig:mfpt_curves_brownian}
+%  \end{subfigure}
+  \caption{(a) The single particle solute flux decays with increasing pore length. 
+  Solutes with high MSDs have higher fluxes. (b) We fit the single particle solute flux 
+  versus pore length, $L$, to a power law function of the form $cL^{-\beta}$ (dashed 
+  lines in (a)). Solutes with higher fluxes have higher values of $c$. Solutes with 
+  smaller Hurst parameters, $H$, have larger values of $\beta$. (c) If we remove 
+  correlation between hops (set $H$=0.5), the flux increases significantly and 
+  $\beta$ is constant at about 2 for all solutes independent of dwell distribution
+  parameters.}\label{fig:flux_curves}
   \end{figure}
 
-  Comparison of Figures~\ref{fig:mfpt_curves_regular} and~\ref{fig:mfpt_curves_brownian}
-  highlights that anti-correlation between hops plays a major role in solute passage times.
-  With a pore length of 50 nm, the MFPT of the fasted moving solute, ethylene glycol is 
-  c.a. 5 times higher with versus without anti-correlated hops. The MFPTs of the slowest
-  moving solute, acetic acid, are about 16 times higher by the same comparison. This 
-  difference will only grow with increasing pore length.
-
-  In Figure~\ref{fig:frac_pore}, we show that solutes which spend more time in the tails
-  tend to have lower Hurst parameters. The densely packed, viscoelastic alkane chains 
-  bounce solutes between them, severely limiting their mobility. Designing LLC membranes
-  that can control or prevent the partition of solutes into the tails may offer the highest
-  returns on membrane performance.
+  % Partially in methods?
+  The power law decay of the flux with pore length implies the following relationship
+  for selectivity via substitution of Equation~\ref{eqn:flux_decay} into 
+  Equation~\ref{eqn:selectivity}:
+  \begin{equation}
+  S_{ij}(L) = \bigg(\frac{c_i}{c_j}\bigg)L^{(\beta_i - \beta_j)}
+  \label{eqn:selectivity_ratio}
+  \end{equation}
+
+  In Figure~\ref{fig:selectivity}, we plot Equation~\ref{eqn:selectivity_ratio} for pore
+  lengths ranging from those studied in Figure~\ref{fig:flux_curves} to macroscopic-length
+  pores. Greater differences in $\beta$ values leads to selectivities that are stronger 
+  functions of pore length. For $(c_i / c_j)=1$, LLC membranes will be more selective
+  towards passage of solutes with lower $\beta$ values versus those with high $\beta$ values.
+  When $\beta$ values are equal, as is the case for uncorrelated motion, selectivity only
+  depends on the pre-factors, $c$.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{selectivity.pdf}
+  \caption{The selectivity of 2 species changes monotonically with pore length. The
+  strength of dependence on pore length depends on the difference between $\beta$ values.}
+  \label{fig:selectivity}
+  \end{figure}
+
+  Out of the solutes studied, the data suggests that this particular LLC membrane 
+  would be most useful for selectively separating ethylene glycol from methanol and 
+  acetic acid. 
+  %It also shows reasonable selectivity of Urea over acetic acid.  
+  Ethylene glycol has the highest $c$ value and the lowest $\beta$ value. The high
+  value of $c$ itself greatly enhances its selective passage. Even more importantly,
+  the relatively large difference between its $\beta$ value and those of methanol 
+  and acetic acid give rise to a strong pore length dependence. The selectivity is
+  enhanced as the pore length increases at the cost of lower solute flux, a 
+  phenomenon ubiquitous in polymer separations membranes.~\cite{geise_water_2011}
+
+  Of course, this approach to modeling LLC membrane selectivity neglects a number of
+  factors that influence real-world aqueous membrane separations. The most glaring is 
+  that we neglected convective flux which should work to increase overall solute flux 
+  and lower selectivity (see Equation ~\ref{eqn:solute_flux}). Defects in the pore 
+  structure will have a strong influence on solute flux which may exacerbate the length 
+  dependence of flux. Even in a perfectly structured membrane, the barrier to pore
+  entry from the bulk solution will have its own influence on experimentally observed 
+  selectivities. This energetic barrier can be made even worse by foulants deposited on
+  the membrane's surface. Therefore, our predictions should be primarily used to 
+  identify the most promising types of selective separations for an H\textsubscript{II}
+  LLC membrane made from a specific monomer.
+  %BJC: though about mentioning fouli
+
+    Neglects concentration polarization, membrane defects and fouling.
+
+%  BJC4: Uncomment to see MFPT curves
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
+%  \caption{Correlated Hops}\label{fig:mfpt_curves_regular}
+%  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
+%  \caption{Uncorrelated Hops}\label{fig:mfpt_curves_brownian}
+%  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{frac_pore.pdf}  % This figure might fit in earlier
+%  \caption{}\label{fig:frac_pore}
+%  \end{subfigure}
+%  \caption{(a) We fit the MFPT versus pore length to a function of the form $cL^{\alpha}$. 
+%  The MFPT grows super-linearly with increasing pore length. Solutes with lower MSDs have
+%  higher MFPTs. (b) If we remove correlation between hops, the MFPTs reduce significantly
+%  and the growth exponent stays constant at 2 for all solutes independent of dwell
+%  distribution parameters. Higher degrees of anti-correlation (lower $H$) lead to higher
+%  growth exponents. (c) Solutes that spend a large fraction of their time in the tails tend
+%  to have larger Hurst parameters.}\label{fig:mfpt_curves}
+%  \end{figure}
+
+%  In Figure~\ref{fig:frac_pore}, we show that solutes which spend more time in the tails
+%  tend to have lower Hurst parameters. The densely packed, viscoelastic alkane chains 
+%  bounce solutes between them, severely limiting their mobility. Designing LLC membranes
+%  that can control or prevent the partition of solutes into the tails may offer the highest
+%  returns on membrane performance.
 

### 2019-12-11 Ben_Manuscripts/stochastic_transport/Draft.tex
New figures and analysis to paper. Parallelization to scripts

@@
   macroscopic properties. We use two different stochastic time series models,
-  parameterized from long molecular dynamics (MD) simulation trajectories, in
-  order to predict solute mean squared displacements (MSDs) and mean first 
-  passage times (MFPTs) in macroscopic length pores. With our first model, 
-  based on the anomalous diffusion theory, we show how solute dynamics can be
-  modeled as a fractional diffusion process subordinate to a continuous time 
-  random walk. From the MD simulations, we parameterize the distribution of 
+  parameterized from long molecular dynamics (MD) simulation trajectories of
+  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
+  membrane, in order to predict solute mean squared displacements (MSDs) 
+  and solute flux in macroscopic length pores. With our first model, based on 
+  the anomalous diffusion theory, we show how solute dynamics can be modeled 
+  as a fractional diffusion process subordinate to a continuous time random 
+  walk. From the MD simulations, we parameterize the distribution of 
   dwell times, hop lengths between dwells and correlation between hops. We 
@@
   applies a single set of parameters to the solute displacements and the second
-  applies 2 sets of parameters based on the solute's radial distance from the closest pore center.
-  Our second model, a generalization of Markov state models, treats the configurational
-  state of the system as a Markov process, each of which has state dependent 
-  transport behavior. For each state and transition between states, we parameterize
-  the distribution and temporal correlation structure of positional fluctuations as
-  a means of characterization and to allow us to predict solute MSDs.
-  We show that our models reasonably reproduce MSDs calculated from molecular 
-  simulations. The anomalous diffusion model shows superior predictive performance, 
-  in many cases reproducing MD results well within error. Finally, we demonstrate 
-  how one can use our models in order to calculate mean first passage time, and 
-  therefore solute flux, of a given solute across a macroscopic-length pore. Overall,
-  this works helps connect the relationship between microscopic chemically-dependent
+  applies 2 sets of parameters based on the solute's radial distance from the
+  closest pore center. Our second model, a generalization of Markov state models,
+  treats the configurational state of the system as a Markov process, each of
+  which has state dependent transport behavior. For each state and transition
+  between states, we parameterize the distribution and temporal correlation 
+  structure of positional fluctuations as a means of characterization and to 
+  allow us to predict solute MSDs. We show that our models reasonably reproduce
+  MSDs calculated from MD simulations. The anomalous diffusion model shows 
+  superior predictive performance, in many cases reproducing MD results well
+  within error. Finally, we demonstrate how one can use our models in order to
+  calculate flux of a given solute across a macroscopic-length pore and, based on 
+  those quantities, the membrane's selectivity towards each solute. Overall, this
+  work helps connect the relationship between microscopic chemically-dependent
   solute motions and macroscopic membrane performance.
 
-%  Finally, we use the 
-%  parameters of each model to identify specific differences in solute transport
-%  behavior which can help suggest modifications that can be made to LLC membrane 
-%  monomers in order to increase or reduce selectivity towards a specific solute
-%  or class of solutes.
-
   \end{abstract}
@@
 
-  Mathematical descriptions of transport in complex separations membranes are 
-  a powerful way to understand mechanisms and formulate membrane design principles. 
-  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
-  The complexity of a model generally parallels the complexity of the transport 
-  mechanism at hand, as well as the transport information the model conveys.
-  In dense homogeneous membranes, the solution-diffusion model can extract 
-  diffusion and partition coefficients and has successfully predicted solute 
-  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
-  models yield predictions of diffusion coefficients and solute transport rates 
-  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
-  tracking approaches take us beyond continuum modeling and allow us to 
-  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
-  level, one can use molecular dynamics (MD) simulations to study both single 
-  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
-  All of these approaches facilitate speculation on the molecular origins of separations
-  by attempting to give a more intuitive understanding of how solutes move as a function
-  of their environment, in turn suggesting experiments that could be performed.
+%  BJC4: Moved this paragraph to later
+%  Mathematical descriptions of transport in complex separations membranes are 
+%  a powerful way to understand mechanisms and formulate membrane design principles. 
+%  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
+%  The complexity of a model generally parallels the complexity of the transport 
+%  mechanism at hand, as well as the transport information the model conveys.
+%  In dense homogeneous membranes, the solution-diffusion model can extract 
+%  diffusion and partition coefficients and has successfully predicted solute 
+%  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
+%  models yield predictions of diffusion coefficients and solute transport rates 
+%  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
+%  tracking approaches take us beyond continuum modeling and allow us to 
+%  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
+%  level, one can use molecular dynamics (MD) simulations to study both single 
+%  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
+%  All of these approaches facilitate speculation on the molecular origins of separations
+%  by attempting to give a more intuitive understanding of how solutes move as a function
+%  of their environment, in turn suggesting experiments that could be performed.
 
@@
   and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
-  there is a strong interest in creating breathable barriers to chemical warfare agents
+  %BJC4: made more general. 
+  there is a strong interest in creating breathable fabrics % barriers 
+  % to chemical warfare agents
   which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
-  The speed at which we achieve these or any other selective separation will be 
-  heavily influenced by the quality of insights gained by the modeling approaches above.
+%  The pace at which we achieve these or any other selective separation goals will be 
+%  heavily influenced by the quality of insights gained by the modeling approaches above.
 
@@
   cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
-  LLC membranes have the potential to disrupt conventional membrane separation techniques by 
-  being selective based not only on size and charge, but on solute chemical functionality
-  as well.~\cite{dischinger_application_2017} One can tune the functionality of LLC monomers
+  They may provide a promising alternative to 
+  % have the potential to disrupt
+  conventional membrane separation techniques by being selective based not only on solute
+  size and charge, but on solute chemical functionality as well.~\cite{dischinger_application_2017}
+  One can tune the functionality of LLC monomers
   in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
@@
   interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
-  its pore structure may decrease a Q\textsubscript{I} membrane's permeability, it is considerably
-  easier to synthesize.
-
-  Molecular modeling may make it possible to efficiently create solute-specific separation
+  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
+  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.
+
+  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
   membranes using the available chemical space of LLC monomers. To date, only a limited 
-  subset of LLC monomers have been studied in membrane applications.
+  subset of LLC monomers have been studied experimentally in membrane applications.
   \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
@@
   could provide quantitative predictions of macroscopic observables such as solute 
-  flux. Due to the size of the system we are studying ($\sim$62,000 atoms) it is 
-  prohibitively expensive and time-consuming to run simulations longer than 
+  flux and selectivity. Due to the size of the types of systems we are studying (at least 62,000 atoms)
+  it is prohibitively expensive and time-consuming to run simulations longer than 
   those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
@@
   timescale predictions. We are in need of a way of studying the collective motion
-  of a much larger set of solute over much longer timescales.
-
-  By reducing our MD simulations to observations of several key properties that 
-  have the greatest influence on solute dynamics, we can construct many realizations
-  of single solute trajectories useful for making long timescale predictions with 
-  computational ease and lower uncertainties. Fortunately, there is an abundance of 
-  information encoded in the complex solute trajectories. Into our model, we can 
-  incorporate fluctuations and time-dependent correlations in solute position as well
-  as the length of time solutes are trapped. We can add further detail by integrating
-  our time series analysis with our knowledge of the primary trapping mechanisms as
-  well as the solute's changing chemical environment within the heterogeneous membrane.
+  of a much larger set of solutes over much longer timescales.
+
+  %BJC4: 1st paragraph moved to here
+  Mathematical descriptions of transport in complex separations membranes are 
+  a powerful way to understand mechanisms and formulate design principles. 
+  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
+  The complexity of a well-fit model generally parallels the complexity of the transport 
+  mechanism at hand, as well as the transport information the model conveys.
+  In dense homogeneous membranes, the solution-diffusion model can extract 
+  diffusion and partition coefficients and has successfully predicted solute 
+  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
+  models yield predictions of diffusion coefficients and solute transport rates 
+  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
+  tracking approaches have taken researchers beyond continuum modeling allowing them to 
+  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
+  level, one can use molecular dynamics (MD) simulations to study both single 
+  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
+  All of these approaches facilitate generation of hypotheses about the
+  molecular origins of separations by attempting to give a more intuitive 
+  understanding of how solutes move as a function of their environment, in turn
+  suggesting experiments that could be performed.
+
+  %BJC4: Tried to make this paragraph connect to previous a little better
+  Using a bottom-up modeling approach, we can parameterize single particle behavior
+  by reducing our MD simulations to observations of several key properties
+  that have the greatest influence on solute dynamics and then construct an ensemble 
+  of characteristic single solute trajectories useful for making long timescale
+  predictions with computational ease and lower uncertainties. Fortunately, there 
+  is an abundance of information encoded in the complex solute trajectories. Into a
+  model, we can incorporate fluctuations and time-dependent correlations in solute
+  position as well as the length of time solutes are trapped. We can add further
+  detail by integrating our time series analysis with our knowledge of the primary
+  trapping mechanisms as well as the solute's changing chemical environment within
+  the heterogeneous membrane.
+
+%  By reducing our MD simulations to observations of several key properties that 
+%  have the greatest influence on solute dynamics, we can construct many realizations
+%  of single solute trajectories useful for making long timescale predictions with 
+%  computational ease and lower uncertainties. Fortunately, there is an abundance of 
+%  information encoded in the complex solute trajectories. Into a model, we can 
+%  incorporate fluctuations and time-dependent correlations in solute position as well
+%  as the length of time solutes are trapped. We can add further detail by integrating
+%  our time series analysis with our knowledge of the primary trapping mechanisms as
+%  well as the solute's changing chemical environment within the heterogeneous membrane.
 
   In this work, we use the output of our MD simulations to construct two new classes of 
-  mathematical models which can predict membrane performance while providing quantitative 
+  mathematical models which aim to predict membrane performance while providing quantitative 
   mechanistic insights. The functional form of these models is driven by mechanistic 
@@
   to a CTRW, or subordinated FBM (sFBM) for short. We fit sFBM
-  models in two ways: 
-  %MRS4: can you clarify the sentence below? Probably something like: uses a single set of parameters in the diffusion equations, etc.
-  %BJC4: see if below helps.
-  %First, based on a single set of parameters. 
-  First, we parameterized solute motion using a single set of parameters fit
+  models in two ways: First, we parameterized solute motion using a single set of parameters fit
   to a hypothesized anomalous diffusion model. Second, we used a two-state approach
   by extracting two sets of model parameters calculated based on a solute's radial
-  distance from the closest pore center. We observe different dynamical behavior of
-  solute within the pore region versus within the monomer tails.
+  distance from the closest pore center. This allows us to include different dynamical
+  behavior of solutes observed within the pore region versus within the monomer tails.
 
@@
   particle trajectories and in addition to providing an easy and efficient way to 
-  simulate solute trajectories, can be helpful in uncovering the underlying 
-  solute-membrane interactions which result in observed transport mechanisms.
-  It can help researchers formulate hypotheses to explain why a certain set of
-  parameters is characteristic to a specific solute. This is largely the approach
-  we used to discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
+  simulate solute trajectories, can help uncover the underlying solute-membrane
+  interactions which result in observed transport mechanisms. It can help 
+  researchers formulate hypotheses to explain why a certain set of parameters is
+  characteristic to a specific solute. This is largely the approach we used to
+  discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
   Once one has knowledge of the primary mechanisms leading to anomalous diffusion
   behavior, one may gain additional insight by formulating a state-based model.
-
-  %BJC4: Replaced below paragraph with above. 
-%  While elegant, pure anomalous diffusion theory may in some cases give only a 
-%  qualitative understanding of transport mechanisms. 
-%  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
-%  %Relating it to molecular scale behavior and examples might help.
-%  %BJC4: mention ageing
-%  %BJC4: ?
-%  Complex temporal relationships in 
-%  between hops may have a significant effect on the average MSD. Inhomogeneity of 
-%  a medium or multiple types of interactions may lead to a number of distinct 
-%  diffusive regimes. In this case, a state based model may be useful.
-
-%  \noindent We can use the observations of transport from our previous work in order to create 
-%  state-based models.
-%  \begin{itemize}
-%  	\item We know that dynamics differ between solutes moving inside the pores and 
-%  	in the tails.
-%  	\item We can use the anomalous diffusion approach to model our data as a 
-%  	function of radial distance from the closest pore center.
-%  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
-%  	methods of Markov state modeling.
-%  \end{itemize}
 
@@
   Our second modeling approach applies an extended MSM framework to a relatively 
-  small set of known states based on the three observed solute trapping mechanisms.  
-  Standard MSMs are typically applied towards determining equilibrium populations
-  of and the transitions between various state configurations.~\cite{bowman_using_2009} 
-  %MRS4: this probably needs to be explained more explicitly, that the coordinates 
-  %of the solute are generated according to the current state. 
-  %BJC4: made more explicit.
-  %We extend the framework
-  %to include dynamics within states and between jumps. 
+  small set of known states based on the three previously observed solute trapping mechanisms.  
+  Standard MSMs are typically applied to determine equilibrium populations
+  of and the kinetics of transitions between various state configurations.~\cite{bowman_using_2009} 
   We extend the framework to include state-dependent fluctuations and correlations in 
-  solute position. 
-  %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
-  %BJC4: rephrased
-%  That is we parameterize 
-%  and incorporate into our model the magnitude and temporal correlation of
-%  fluctuations in solute position while in each state as well as during transitions
-%  to different states. 
-  That is the magnitudes of a solute's fluctuations from its average trapped 
+  solute position. The magnitudes of a solute's fluctuations from its average trapped 
   position and the degree of correlation with its previous fluctuations is 
-  defined by the parameters of its current state. To distinguish our approach from
-  standard MSMs, we have named it the Markov state-dependent dynamical model (MSDDM).
-  %BJC4: Added name of our modeling approach in last sentence
+  determined by the current state. To distinguish our approach from standard MSMs, we have
+  named it the Markov state-dependent dynamical model (MSDDM).
 
   %BJC4: making goals more explicit
-  The success of our modeling approaches can be defined in two ways. First, if we
-  can closely reproduce solute MSDs measured from MD simulations with realizations
+  We determine the degree of success of our modeling approaches in two ways. First,
+  if we can closely reproduce solute MSDs measured from MD simulations with realizations
   of our models, then it is likely that the model sufficiently captures solute 
@@
   of choosing the correct anomalous subdiffusion provides its own mechanistic insight
-  since it requires a thorough analysis of solute time series behavior. One can then
-  screen different solutes, compare the fit model parameters and relate them back to 
+  since it requires a thorough analysis of solute time series behavior. One can simulate
+  different solutes, compare the fit model parameters and relate them back to 
   differences in solute size and chemical composition. The MSDDM characterizes 
@@
 
-  %BJC4: new
-  We find that the sFBM anomalous diffusion model does the best job of reproducing
-  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
-  how one could predict solute flux through a theoretical pore of with an 
-  experimentally relevant length.
+  Finally, we use our most promising model in order to predict solute flux and 
+  selectivity in pores of macroscopic length, thus achieving a better understanding
+  of macroscopic properties on the basis of microscopic dynamics. We show that 
+  anti-correlated solute hopping behavior severely reduces flux relative to 
+  uncorrelated behavior. We use the relative solute fluxes to calculate the 
+  membrane's selectivity between all pairs of solutes and demonstrate that, when 
+  solutes display different degrees of anti-correlated hopping behavior, selectivity
+  becomes a function of pore length. With this improved understanding of 
+  macroscopic behavior, we can begin to think more critically about how to design 
+  membranes in order to selectively pass or reject specific solutes.
+
+%  We find that the sFBM anomalous diffusion model does the best job of reproducing
+%  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
+%  how one could predict solute flux through a theoretical pore of with an 
+%  experimentally relevant length.
 
@@
 
-  We ran all MD simulations and energy minimizations using GROMACS 2018. 
+  We ran all MD simulations and energy minimizations using GROMACS 2018.  %BJC4: version 2018. That's it not 2018.3 or anything. 
   ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
@@
   pore and tail region reached apparent equilibrium and use only data after that point
-  in our analysis of solute kinetics. We plotted the solute partition versus time in
+  in our analysis of solute kinetics. We plot the solute partition versus time in
   Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify 
@@
 
-  % BJC3: x --> z since I'm measuring diffusion in the z direction?
-  % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
-  % BJC4: I think it'll be less confusing to me writing it to change it to z.
   Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
   During an anomalous diffusion process, the mean squared displacement (MSD)
-  does not grow linearly with time, rather it follows a power law of the form:
+  does not grow linearly with time, but instead it follows a power law of the form:
   \begin{equation} 
@@
 
-  %BJC3: removed ensemble MSD because it's not used
   We analyzed the time-averaged MSD of the simulated trajectories by measuring
@@
   where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
-  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. 
-  %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
-  %BJC4: reworded, defined ergodicity (usually called 'weak' ergodicity breaking in literature) and
-  % explained why it's not important for this study.
+  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
+  MSD is given by:
+  \begin{equation}
+  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
+  \label{eqn:ensemble_msd}
+  \end{equation} 
   In a pure CTRW, for example, the power law distribution of trapping times leads to
@@
   measurement time scale of solute motion. In fact, as measurement time increases, the 
-  MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
+  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
   with trapping times on the order of the measurement time get incorporated into the 
@@
 
-  \subsubsection*{Subordinated Fractional Brownian Motion}
-
-  The solute motion in the system studied here may be consistent with 
-  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
-  the leading process is a CTRW. We observe hopping and trapping which is consistent
-  with a CTRW, along with negatively correlated hops which is consistent with FBM.
-
-  One can characterize a CTRW process by the parameters which describe its dwell 
-  time and hop length distributions. We used the \texttt{ruptures} python package in 
-  order to automatically identify mean shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018} 
-  We used the corresponding hop lengths and dwell times between hops to construct 
-  empirical distributions.
+  \subsubsection{Subordinated Fractional Brownian Motion}\label{method:sfbm}
+
+%  BJC4: I say something to the following effect in the intro
+%  The solute motion in the system studied here may be consistent with 
+%  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
+%  the leading process is a CTRW. We observe hopping and trapping which is consistent
+%  with a CTRW, along with negatively correlated hops which is consistent with FBM.
+
+%  We modeled solute motion as a continuous time random walk (CTRW) subordinate to 
+%  fractional Brownian motion, also called subordinated fractional Brownian motion (sFBM).
+%  We modeled solute motion as a CTRW subordinate to FBM, also called sFBM.
+
+  One can characterize the CTRW component of an sFBM process by the parameters which describe
+  its dwell time and hop length distributions. We used the \texttt{ruptures} python
+  package in order to automatically identify mean shifts in solute trajectories, 
+  indicating hops.\cite{truong_ruptures:_2018} We used the corresponding hop lengths
+  and dwell times between hops to construct empirical distributions.
 
@@
   proportional to $t^{-1-\alpha_d}$.~\cite{meroz_toolbox_2015}
-  %BJC3: is it okay to leave above equation in line? Or should it get numbered?
-  %BJC3: I added subscript d to the dwell time alpha because alpha is a standard parameter for power laws and levy stable distributions
-% BJC3: following includes normalization constant 
-%  of the form:
-%  \begin{equation}
-%  (\beta - 1)x_{min}^{\beta - 1}x^{-\beta}
-%  \end{equation}  
-%  where $\beta = (1 + \alpha)$ and $x_{min}$ is the smallest measured value of $x_i$.~\cite{meroz_toolbox_2015,clauset_power-law_2009}
-%  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
   Because we are limited to taking measurements at discrete intervals dictated by the output 
@@
   to a discrete power law distribution whose maximum likelihood $\alpha_d$ 
-  parameter we calculated by maximizing the following likelihood function: 
+  parameter we calculated by maximizing the likelihood function: 
   \begin{equation}
@@
   In practical applications, the heavy tail of power law distributions can result in 
-  arbitrarily long dwell times that are never observed in MD simulations. We can not
+  arbitrarily long dwell times that are never observed in MD simulations. We cannot
   observe dwell times longer than the length of a single trajectory. 
-  % Could be an interesting factoid, but not necessary 
-  % In fact, the longest dwell time observed by any solute in this study is X. 
   In order to directly compare our anomalous diffusion model to finite-length MD 
-  trajectories we may need to bound the dwell time distribution. We do this by adding 
+  trajectories we need to bound the dwell time distribution. We do this by adding 
   an exponential cut-off to the power law so the dwell time distribution is 
@@
   The measured mean is always very close to zero so we assume that it is exactly zero
-  in our time series simulations since we have no reason to expect drift in either direction.
+  in our time series simulations since we have no reason to expect drift in either direction
+  based on pore symmetry.
 
@@
   are so close to zero. Therefore, we obtained H by performing a least squares fit of 
-  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 lags of the empirically measured
-  autocorrelation function.
-
-  \subsubsection*{Subordinated Fractional L\'evy Motion}
+  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 400 ps time lags of the 
+  empirically measured autocorrelation function.
+
+  \subsubsection{Subordinated Fractional L\'evy Motion}\label{method:sflm}
 
@@
   deviate from the empirically measured PDF (see Section~\ref{S-section:truncation}
-  of the Supporting Information).
-
-  % BJC3: maybe a table of cut-offs used here. We will see how close they are. Might
-  % use the same for all.
-
-  %MRS4: should be more clear which of the two kinetics scenarios this next assumption applies to
-  %BJC4: changed title to clarify that this is anomalous diffusion
+  of the Supporting Information).~\cite{mantegna_stochastic_1994}
+
   \subsubsection*{Multiple Anomalous Diffusion Regimes}
@@
   We observe different dynamical behavior when solutes move while inside 
-  the pore versus while in the tail region. This inspired two anomalous diffusion 
+  the pore versus while in the tail region. This suggest two anomalous diffusion 
   models of varying complexity. We created a simple, single mode model with a single 
@@
   All models include correlation between hops.
-  %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
-  %BJC4: made table
+
   \begin{table}[!htb]
@@
 
-  \subsection{Markov State-Dependent Dynamics}\label{method:MSMs}
+  \subsection{The Markov State-Dependent Dynamical Model}\label{method:MSMs}
 
@@
   discrete states. The states we have chosen include all combinations of trapping
-  mechanisms in the pore and out of the pore (see Table~\ref{table:states}). We use
-  the same radial cut-off (0.75 nm) as in the anomalous diffusion model to differentiate
-  the pore and tail region. These state choices assume that there are no significant
-  kinetic effects resulting from solute conformational changes or pore size fluctuations,
-  an assumption that may be relaxed in future work.
+  mechanisms in the pore and out of the pore (see Table~\ref{table:states}). They
+  assume that there are no significant kinetic effects resulting from solute 
+  conformational changes or pore size fluctuations, an assumption that may be 
+  relaxed in future work. We use the same radial cut-off (0.75 nm) as in the 
+  anomalous diffusion model to differentiate the pore and tail region.  We define 
+  a hydrogen bond to exist if the distance between donor, D, and acceptor, A, 
+  atoms is less than 3.5 \AA~and the angle formed by $D-H \cdots A$ is less than
+  30$\degree$. We define a sodium ion to be associated with an atom if they are 
+  within 2.5 \AA~of each other.~\cite{coscia_chemically_2019}
 
@@
 	  \caption{We defined 8 discrete states based on all combinations of previously observed solute
-	  trapping mechanisms}\label{table:states}  
+	  trapping mechanisms.}\label{table:states}  
 	  %BJC3: the caption will depend on the journal. I don't
@@
   transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
-  test is to verify that $T$ holds up to coarser time scales. As long as solutes
+  test is to verify that $T$ holds up to coarser time scale partitioning. As long as solutes
   sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
@@
   overall configurational state of the solute and it's environments. 
-  While MSMs are often used to gauge equilibrium populations of various states, adding 
-  %MRS4: it's not just ``dynamics'', though, it's a specific subset of the dynamics.  
-  % And one could argue that the MSMs are being added to the dynamics, since the time trace is the desired output, 
-  % rather than the output one usually gets from MSMs.
-  %BJC4: made more specific with 'state-dependent dynamics' instead of just 'dynamics'
-  %BJC4: confusion here
+  While MSMs are often used to estimate equilibrium populations of various states, adding 
   state-dependent dynamics allows us to more accurately simulate solute trajectories.
@@
 
-  We observed negatively correlated hops within each state and among transitions between
-  states. We can use the Hurst parameter to describe this negative time series correlation
-  however, there is not sufficient data to accurately measure a Hurst parameter for 
+  We use the Hurst parameter to describe this negative time series correlation.
+  However, there is not sufficient data to accurately measure a Hurst parameter for 
   each type of transition. We avoided this problem by treating transitions as correlated
   emissions from a single L\'evy stable distribution. This reduces the number of emission
-  distributions from 64 to 9 (1 for each state and 1 for transitions between states).
+  distributions from 64 to 9 (1 for each of the 8 states and 1 for transitions between states).
+
+%  We observed negatively correlated hops within each state and among transitions between
+%  states. We can use the Hurst parameter to describe this negative time series correlation
+%  however, there is not sufficient data to accurately measure a Hurst parameter for 
+%  each type of transition. We avoided this problem by treating transitions as correlated
+%  emissions from a single L\'evy stable distribution. This reduces the number of emission
+%  distributions from 64 to 9 (1 for each state and 1 for transitions between states).
 
@@
   corresponding to the particle's current state. Again, because we are working with a
-  finite data set, we incorporated uncertainty into the rows of the transition matrix 
-  by resampling them from a Dirichlet distribution. For each same-state subsequence of
-  the full state sequence, we simulated an FLM process using the Hurst parameter of that
-  state and the parameters of the corresponding emission distribution. Independently, 
-  we simulated the transition between each same-state sequence with an FLM process 
-  based on the Hurst parameter of transition sequences and the parameters of the 
-  single transition emission distribution. We used the same FLM simulation procedure
-  described in Section~\ref{method:model_sFBM}.
+  finite data set, we incorporated transition probability uncertainties into the rows
+  of the transition matrix by resampling them from a Dirichlet distribution. For each 
+  same-state subsequence of the full state sequence, we simulated an FLM process using
+  the Hurst parameter of that state and the parameters of the corresponding emission
+  distribution. Independently, we simulated the transition between each same-state 
+  sequence with an FLM process based on the Hurst parameter of transition sequences 
+  and the parameters of the single transition emission distribution. We used the same
+  FLM simulation procedure described in Section~\ref{method:model_sFBM}.
 
@@
 
-  We used the ratio of solute fluxes in order to determine membrane selectivity, $S$,
+  We used the ratio of solute fluxes in order to determine membrane selectivity, $S_{ij}$,
   towards solutes. Selectivity of solute $i$ versus $j$ is defined in terms of the
@@
   \begin{equation}
-  J_v = L_p(\Delta P - \Delta \pi)
+  J_v = L_p(\Delta P - \sigma\Delta \pi)
   \end{equation} 
@@
 
+  \subsubsection{Parameterizing Subordinated Fractional Brownian Motion}\label{section:AD_parameterization}
+
   The evidence suggests that solutes in this system can be well-modeled by subordinated
-  fractional Brownian motion. The solutes clearly perform jumps after periods of relative
+  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use Urea to
+  support this claim. Analogous figures for all other solutes are presented in the Supporting
+  Information, Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops}.
+  The solutes clearly perform jumps after periods of relative
   immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
@@
   the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
-  The parameter estimates describing our 1 and 2 mode models are summarized in 
-  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} (also trying it out in 
-  Figures~\ref{fig:radars} and~\ref{fig:radars_nolines})
+  The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
+  summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
 
@@
   \end{subfigure}
-  \caption{(a) Urea exhibit hops between periods of entrapment, characteristic of a CTRW. 
+  \caption{(a) Urea exhibits hops between periods of entrapment, characteristic of a CTRW. 
   (b) The distribution of hop lengths fits well to a Gaussian as well as a more general L\'evy 
@@
   hop. In combination, (a) -- (d) support modeling solutes as subordinated fractional Brownian
-  motion. The behavior shown by urea in this figure is common to all solutes in this study.}\label{fig:anticorrelated_hops}
+  motion. The behavior shown by urea in this figure is common to all solutes in this study (see
+  Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops} of the
+  Supporting Information).}\label{fig:anticorrelated_hops}
   %MRS4: are there similar figures in the supporting information.
-  %BJC4: no but I can make them
+  %BJC4: added
   \end{figure}
@@
 
-  % BJC3: is it worth trying to combine these tables?
-  % BJC: note to self -- modes are flipped in simulation output because 
-  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
+  \subsubsection{Model validation on stationary trajectories}\label{section:sfbm_validation}
+
+  We evaluated the predictive capabilities of the AD modeling approach by training
+  the model parameters on the first half of the equilibrated MD trajectory data and
+  then comparing the MSD calculated from AD model realizations to the MSD calculated
+  from the second half of the equilibrated MD trajectory data. This metric is
+  only meaningful if the ensemble of solute trajectories is stationary.
+
+  We observe that in many cases, the distribution of solutes within the membrane
+  evolves slowly with time. We defined the perceived equilibration time point 
+  for each solute based on the time at which the number of solutes inside the
+  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
+  solute behavior after equilibration, on the $\mu$s timescale. In Table~\ref{table:stationarity},
+  we compare the MSD of the solutes calculated using trajectory data from the 
+  first and second halves of the equilibrated simulation time. Ethylene glycol 
+  and methanol show considerable differences in their MSDs. Urea and acetic acid
+  appear to demonstrate satisfactory stationarity on the 5 $\mu$s timescale. The
+  shapes of their MSDs curves are also very similar (see Figure~\ref{S-fig:msd_comparison}
+  of the Supporting Information).
+
   \begin{table}[h]
   \centering
-  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
+  \begin{tabular}{|c|c|c|}
   \hline
-  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
-  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
-  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
-  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
-  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
-  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
-  \hline 
+  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
+                           & First Half       & Second Half      \\\hline
+  Urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
+  Ethylene Glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
+  Methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
+  Acetic Acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
+
   \end{tabular}
-  \caption{To create a 1 mode model for each solute, we parameterized a pure power
-  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
-  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
-  law tails and higher values of $\lambda$ truncate the distribution at lower
-  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
-  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
-  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
-  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
-  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
-  function ($\gamma(H)$) to describe the degree of correlation between hops. 
-  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
+  \caption{In order to be considered stationary, the MSD of the ensemble of solute trajectories
+  should be the same independent of the portion of equilibrated trajectory that is
+  analyzed. The MSD values in this table are averages taken after a 500 ns time lag, 
+  calculated independently from the first and second halves of the equilibrated
+  solute trajectories. Urea and acetic acid both appear to satisfy the stationarity
+  criteria, while ethylene glycol and methanol show significantly smaller MSDs 
+  when calculated from the second half of the equilibrated trajectories.}\label{table:stationarity}
   \end{table}
 
-  \begin{table}[h]
+  %BJC4: need figures to support these claims.
+  The non-stationary behavior of ethylene glycol and methanol present themselves
+  in different ways. On average, methanol molecules in the tails appear to be 
+  drifting further away from the pore center with time. Methanol's small size 
+  significantly increases the volume of accessible structural space. Ethylene 
+  glycol appears to experience an increased incidence of long trapping times. 
+  These problems probably cannot be addressed without more simulation time or 
+  additional solute trajectories.
+
+  Using the approach described above, we validated our 1 and 2 mode models with
+  urea and acetic acid, since their trajectories appear stationary. The 
+  resultant MSD plots are shown in Figure~\ref{fig:train_test}. We consider 
+  our models to match well if their predictions lie within the 1-$\sigma$
+  confidence intervals of the MD MSDs. We also look for qualitative agreement
+  in the shape of the curves.
+
+  \begin{figure}
   \centering
-  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
-  \hline
-  \multicolumn{7}{|c|}{2 Mode Model} \\\hline
-                & Parameters                               & Mode & Urea         & Ethylene Glycol &  Methanol    & Acetic Acid \\
-  \hline
-                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.90         & 0.58         \\\cline{3-7}
-  Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
-  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.04, 0.0006 & 0.41, 0.0026 \\\cline{3-7}
-                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.30, 0.0054 & 0.00, 0.0021 \\\hline
-                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.45         & 0.32         \\\cline{3-7}
-  Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
-  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.31, 1.97   & 0.21, 1.91   \\\cline{3-7}
-                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.85   & 0.09, 1.50   \\\hline
-  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
-  \hline 
-  \end{tabular}
-  \caption{The two model parameterizes solute behavior in the pores and tails separately. 
-  Generally, movement is much more restricted in the tail region. To create a 2 mode model,
-  we generated a set of parameters based on solute behavior as function of distance from
-  the pore center. Mode 1 corresponds to solute behavior within 0.75 nm of the pore center
-  and mode 2 corresponds to behavior greater than or equal to 0.75 nm from the pore center.
-  Note that we used the same Hurst parameter for both modes due to a low number of 
-  sufficiently long sequences of hops in each mode. See Table~\ref{table:sfbm_params} for
-  descriptions of the parameters.}\label{table:sfbm_params_2mode}
-  \end{table}
-
-  %BJC4: another (bad) way to visualize data
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{1mode_radar.pdf}
-%  \caption{}\label{fig:1mode_radar}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{2mode_radar.pdf}
-%  \caption{}\label{fig:2mode_radar}
-%  \end{subfigure}
-%  \caption{Another way to visualize Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}}\label{fig:radars}
-%  \end{figure}
-%  
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
-%  \caption{}\label{fig:1mode_radar}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{2mode_radar_nolines.png}   % for some reason it has trouble saving this as a PDF
-%  \caption{}\label{fig:2mode_radar}
-%  \end{subfigure}
-%  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
-%  \end{figure}
-
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
-%  \caption{}\label{fig:1mode_radar_nolines}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{2mode_radar_nolines.pdf}
-%  \caption{}\label{fig:2mode_radar_nolines}
-%  \end{subfigure}
-%  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
-%  \end{figure}
-
-  Using the parameters in Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}
-  as inputs to our models, we obtain reasonable predictions of the MD simulated MSDs. The 
-  MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
+  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
+  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
+  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
+  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
+  \end{subfigure} 
+  \caption{In most cases, when using power laws with exponential cut-offs 
+  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
+  the first half of the equilibrated data lie within the 1-$\sigma$ confidence
+  intervals of the MD MSD curves generated from the second half of the equilibrated
+  solute data. The models which use pure power laws systematically under-predict
+  the MD MSD curves. The shape of the MSD curves appear qualitatively correct
+  for urea, but lack curvature in the case of acetic acid.}\label{fig:train_test}
+  \end{figure}
+
+  The models are capable of reasonably predicting the MD MSD values of the second
+  half of the solute trajectories based on parameters generated from the first half
+  when the dwell time distributions are parameterized by a power law with an 
+  exponential cut-off. Without truncation of the power law distribution, the MD 
+  MSDs are underestimated in all cases because dwell times on the order of the
+  MD simulation length are sampled and incorporated into the simulated anomalous
+  diffusion trajectories. Considering the longest observed dwell time among all
+  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
+
+%  We also observe that simulated AD trajectories which draw from a L\'evy stable 
+%  distribution generally predict higher MSDs. The heavy tails of the distribution 
+%  incorporate large jumps more frequently into the trajectories.
+
+  From a qualitative perspective, the models only have moderate success at predicting
+  the shape of the MSD curves. In general, the MSDs generated by our AD models appear
+  close to linear at long time scales. This is expected behavior for time averaged 
+  MSDs, especially when truncating the power law distribution of dwell times.
+  \cite{molina-garcia_crossover_2018} The linearity of Urea's MD MSD curve is 
+  consistent with that of the AD model, but the MD MSD of acetic acid appears to have considerable
+  curvature. Acetic acid's MSD is under-predicted at short timescales but within error 
+  of MD (using sFBMcut and sFLMcut models) after a 500 ns time lag. The curvature suggests that the 
+  model under-estimates long timescale positional anti-correlation which points to an
+  over-estimate of the Hurst parameter. This is not surprising because the Hurst 
+  parameter is challenging to quantify, especially with a relatively small amount of 
+  data (see Section~\ref{method:sfbm} for further discussion of this challenge).
+  A more accurate measurement of $H$ would fix the shape of the MSD curve, but also
+  lower the predicted MSD meaning we are either underestimating the width of the hop
+  length distribution, favoring longer dwell times or both.
+  % BJC4: play around with this to see how to change shape of acetic acid curve. Hurst makes it arc more
+  % ctrwsim.py -alpha 0.08 -fix_time -hop fbm -H 0.34 -ntraj 100 -dwell powerlaw_cutoff -lamb 0.0033 -hs 0.27
+
+  This brief analysis suggests that working with only half of the data we collected
+  ($\sim$2$\mu$s post-equilibration) is not always sufficient for extracting reliable
+  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
+  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
+  sFLMcut). However, in the case of acetic acid, this may only happen because the 
+  Hurst parameter is overestimated. It appears we are operating on the border of the
+  minimum amount of data required to accurately parameterize the AD model. Longer
+  simulations and more independent trajectories may be necessary. Therefore, in 
+  the next section we will work with parameters fit to the full equilibrated portion
+  of the solute trajectories, doubling the data.
+
+%  This brief analysis highlights some of the shortcomings of the AD model. So far, we have 
+%  shown that it does a reasonable job of approximating the magnitude of the MD-MSD
+%  after a 500 ns time lag, but the shape can sometimes be qualitatively wrong because of
+%  inaccurate Hurst parameters. In the case of acetic acid, a poorly measured $H$, but 
+%  accurate prediction of the magnitude of the MSD after 500 ns, may mask underlying 
+%  problems with the parameters of the hop length and dwell time distributions. Acetic
+%  acid has the lowest MSD of the solutes studied, therefore these issues may be resolved
+%  by longer simulations.
+
+  %BJC4: comment here about the length of time simulations need to be run in 
+  % order to get reliable data
+  % Or maybe a little later since acetic acid, although stationary
+  % comment on acetic acid's trajectory shape.
+
+  \subsubsection{Model predictions using all equilibrated data}\label{section:AD_all_data}
+
+  We obtain reasonable predictions of the MD simulated MSDs when we parameterize the
+  AD model with all available data after the perceived equilibration time. We visualized the
+  parameters in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
+  The MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
   comparison in Figures~\ref{fig:anomalous_msds_1mode} and~\ref{fig:anomalous_msds_2mode}
-  respectively. 
-  %The MSD of AD trajectories modeled using a power law with an exponential 
-  %cut-off have a significantly reduced uncertainty and lie well within the error bars of MD.
+  respectively. Although we concluded that methanol and ethylene glycol trajectories are
+  not yet stationary, we include them in all analysis going forward because it is still
+  instructive.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
+  \caption{}\label{fig:1mode_AD_hops}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
+  \caption{}\label{fig:1mode_AD_dwells}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
+  \caption{}\label{fig:hurst_barchart}
+  \end{subfigure}
+  \caption{The parameters of the 1 mode model reveal differences in solute dynamics.
+  (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, and L\'evy stable, 
+  $L(\sigma, \alpha_h)$, distributions to describe solute hop lengths. We assume the 
+  mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta = 0$)
+  in the L\'evy stable disributions. High values of $\sigma$ and lower values of $\alpha_h$
+  result in larger hops. (b) We parameterized a pure power law, $P(\alpha_d)$, and a 
+  truncated power law, $P_T(\alpha_d, \lambda)$, distribution to describe solute dwell
+  times. Lower values of $\alpha_d$ lead to heavier power law tails and higher values of 
+  $\lambda$ truncate the distibution at lower dwell times. (c) Finally, we parameterized the
+  hop autocorrelation function, $\gamma(H)$, to describe the degree of correlation between
+  hops. Higher values of $H$ display closer to Brownian behavior.}\label{fig:1mode_parameters}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.475\textwidth}
+  \includegraphics[width=\textwidth]{2mode_AD_hops.pdf}
+  \caption{}\label{fig:2mode_AD_hops}
+  \end{subfigure}
+  \begin{subfigure}{0.475\textwidth}
+  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
+  \caption{}\label{fig:2mode_AD_dwells}
+  \end{subfigure}
+  \caption{
+  The two mode model parameterizes solute behavior in the pore and tails separately.
+  We consider solutes to be within the pore region if they are 0.75 nm from a given pore
+  center, otherwise they are in the tails. (a) Generally, movement is much more restricted
+  in the tail region shown by lower $\sigma$ values for the Normal and L\'evy stable 
+  distributions. Values of $\alpha$ are significantly lower for urea and acetic acid meaning 
+  there is a larger probability that they will take large hops. (b) Dwell times are longer in 
+  the tails. Lower values of $\alpha_d$ correspond to power laws with heavier tails and 
+  thus higher probabilities of long dwell times. There is no easily discernable trend in
+  $\lambda$ of the truncated power law distribution. Note that we used the same Hurst parameter
+  for both modes (shown in Figure~\ref{fig:hurst_barchart}) due to a low number of 
+  sufficiently long sequences of hops in each mode.}
+  \label{fig:2mode_parameters}
+  \end{figure}
 
@@
 
-  Truncating the power laws with an exponential cut-off has the largest effect on the on 
-  the match between the MD-calculated MSD and that measured from the simulated anomalous
-  diffusion trajectories. Without truncation, the MD MSDs are underestimated in all cases.
-  This is because dwell times on the order of the MD simulation length are sampled and 
-  incorporated into the simulated anomalous diffusion trajectories, reducing the MSD. 
-  The longest observed dwell time among the solutes was 1.3 $\mu$s by ethylene glycol.
-
-  Simulated AD trajectories which draw from a L\'evy stable distribution generally 
-  predict higher MSDs. The heavy tails of the distribution incorporate large
-  jumps more frequently into the trajectories. The only exception is that of ethylene
-  glycol in the 2 mode model where the L\'evy index for both modes is near 2, indicating
-  a near Gaussian distribution.
-  % BJC4: need to explain this somehow.
+  After a 1000 ns time lag, for all solutes except acetic acid, the 1 and 2 mode 
+  AD models do a fairly good job of predicting the magnitude of the MD 
+  MSD curves when we use truncated power laws. In all but one case (two mode 
+  ethylene glycol), MSD curves predicted by the sFLMcut model are higher than 
+  those predicted by the sFBMcut model because of the heavy tails of the L\'evy 
+  stable hop length distribution.
+
+  Qualitatively, the curves with the highest final MSDs (ethylene glycol and 
+  methanol) show more linear growth and their shapes are well captured by the
+  sFLMcut and sFBMcut AD models. The MSD curve of urea bends slightly and 
+  that of acetic acid has the most significant curvature. When the MD MSD 
+  curves bend, the MSD curves predicted by the sFBMcut model tends to more 
+  accurately portray their curvature since the sFLMcut model tends to become 
+  linear faster.
+
+  Acetic acid is a notable exception as no model accurately predicts its
+  MSD or curvature. Both sFBMcut and sFLMcut significantly over-predict the final
+  MSD while sFBM and sFLM significantly under-predict it. Once again, it 
+  appears that the Hurst parameter may be over-estimated. However, the parameters
+  of the hop and dwell distributions may be improved over those used to produce
+  Figures~\ref{fig:1mode_msd_comparison_ACH_train_front} and
+  \ref{fig:2mode_msd_comparison_ACH_train_front}. A lower value of $H$ would 
+  increase the curvature and reduce the AD predicted MSD to values more consistent
+  with acetic acid's MD MSD.
+
+  Despite their deviations from the MD, the ranking of the magnitude of predicted
+  MSDs remains the same as MD: ethylene glycol $\approx$ methanol $>$ urea $>$ acetic acid.
+%  The discrepancies between MD and the predictions of the AD model may be resolved
+%  by gathering longer and a greater quantity of solute trajectories
+  Therefore, we can use the current parameters to understand solute dynamics.
 
@@
   trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
-  relatively similar which is consistent with their similar MD-measured MSDs. Methanol 
+  relatively similar which is consistent with their similar MD MSDs. Methanol 
   tends to stay trapped for less time and takes larger hops but the most substantial
@@
   to make larger jumps to escape traps.
+
+  Overall, the AD model does a reasonable job of predicting solute MSDs and its 
+  parameters can help us further understand solute dynamics. Hops appear to be well
+  modeled as anticorrelated draws from Gaussian and L\'evy stable distributions. 
+  The data strongly suggests that one must truncate the power law dwell time 
+  distributions in order to obtain accurate MSD estimates. We can further understand
+  solute dynamics by adding radially dependent parameter distributions as in the 
+  2 mode model. A significant amount of solute trajectory data is necessary 
+  in order to achieve good parameter estimates. The exact amount of data required 
+  is dependent on the solute studied. Solutes which achieve higher MSDs
+  in a given amount of time appear to be more accurately parameterized.
 
@@
 
-  \subsubsection{Model validation on stationary trajectories}\label{section:sfbm_validation}
-
-  We evaluated the predictive capabilities of the AD modeling approach by training
-  the model parameters on the first half of the equilibrated MD trajectory data
-  then comparing the MSD calculated from AD model realizations to the MSD calculated
-  from the second half of the equilibrated MD trajectory data. This metric is
-  only meaningful if the ensemble of solute trajectories is stationary.
-
-  We observe that in many cases, the distribution of solutes within the membrane
-  evolves slowly with time. We defined the perceived equilibration time point 
-  for each solute based on the time at which the number of solutes inside the
-  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
-  solute behavior after equilibration, on the $\mu$s timescale. In Table~\ref{table:stationarity},
-  we compare the MSD of the solutes calculated using trajectory data from the 
-  first and second halves of the equilibrated simulation time. Ethylene glycol 
-  and methanol show considerable differences in their MSDs. Urea and acetic acid
-  appear to demonstrate satisfactory stationarity on the 5 $\mu$s timescale. The
-  shapes of their MSDs curves are also very similar (see Figure~\ref{S-fig:msd_comparison}
-  of the Supporting Information).
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{|c|c|c|}
-  \hline
-  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
-                           & First Half       & Second Half      \\\hline
-  Urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
-  Ethylene Glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
-  Methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
-  Acetic Acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
-
-  \end{tabular}
-  \caption{In order to be considered stationary, the MSD of the ensemble of solute trajectories
-  should be the same independent of the portion of equilibrated trajectory that is
-  analyzed. The MSD values in this table are averages taken after a 500 ns time lag, 
-  calculated independently from the first and second halves of the equilibrated
-  solute trajectories. Urea and acetic acid both appear to satisfy the stationarity
-  criteria, while ethylene glycol and methanol show significantly smaller MSDs 
-  when calculated from the second half of the equilibrated trajectories.}\label{table:stationarity}
-  \end{table}
-
-  The non-stationary behavior of ethylene glycol and methanol present themselves
-  in different ways. On average, methanol molecules in the tails appear to be 
-  drifting further away from the pore center with time. Methanol's small size 
-  significantly increases the volume of accessible structural space. Ethylene 
-  glycol appears to experience an increased incidence of long trapping times. 
-  These problems probably cannot be addressed without more simulation time or 
-  additional solute trajectories.
-
-  Using the approach described above, we validated our 1 and 2 mode models with
-  urea and acetic acid, since their trajectories appear stationary. The 
-  resultant MSD plots are shown in Figure~\ref{fig:train_test}.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
-  \caption{Urea (1 mode)}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
-  \caption{Urea (2 modes)}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
-  \caption{Acetic acid (1 mode)}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
-  \caption{Acetic acid (2 modes)}
-  \end{subfigure} 
-  \caption{The MSD curves predicted by the AD model trained on the first half 
-  of the equilibrated data closely reproduce the MSD curves generated from the 
-  second half of the equilibrated solute data.}\label{fig:train_test}
-  \end{figure}
-
-  The models reasonably predict the MSD of the second half of the solute 
-  trajectories based on parameters generated from the first half. This success
-  provides increased confidence in our ability to generate useful predictions
-  of long time scale solute behavior
-
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{|M{1.75cm}|M{1cm}|M{1.65cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|}
-%  \hline
-%  \multirow{2}{*}{Solute}&\multirow{2}{*}{Modes}&\multirow{2}{*}{Model}&\multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{4-7}
-%                              &                   &        & MD MSD                & Prediction & MD MSD               & Prediction \\\hline
-%  \multirow{4}{*}{Urea}       & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.43 (1.11, 1.76)}&0.31 (0.28, 0.35)&\multirow{4}{*}{1.43 (1.11, 1.77)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-%                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
-%                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-%                              &                   &sFLMcut&                         &            &                     &            \\\hline
-%                              & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.03 (0.79, 1.29)}        &            &\multirow{4}{*}{1.03 (0.77, 1.30)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-%  Ethylene                    &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
-%  Glycol                      &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-%                              &                   &sFLMcut&                         &            &                     &            \\\hline
-%  \multirow{4}{*}{Methanol}   &\multirow{2}{*}{1} &sFBMcut&\multirow{4}{*}{1.06 (0.69, 1.36)}        &            &\multirow{4}{*}{1.06 (0.67, 1.37)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-%                              &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
-%                              &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-%                              &                   &sFLMcut&                         &            &                     &            \\\hline
-%  \multirow{4}{*}{Acetic Acid}& \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{0.35 (0.28, 0.45)}&0.31 (0.28, 0.35)&\multirow{4}{*}{0.35 (0.26, 0.47)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-%                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
-%                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
-%                              &                   &sFLMcut&                         &            &                     &            \\\hline
-%  \end{tabular}
-%  \caption{}\label{table:sFBM_train}
-%  \end{table}
-
   %BJC3: Is it a bad idea to acknowledge that there is no experimental data? I can 
@@
   %MRS4: also, you need to be more specific about choosing for WHAT purpose.  Different purposes could imply different models.
-  Choosing which model to use for long timescale projections is not entirely obvious
-  without experimental data to compare with. For our comparisons to MD, using a 
-  truncated power law distribution is an obvious choice. However, given that extremely
-  long dwells are a rare event, it is possible that studying a much larger set of 
-  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
-  distributions, the generality of L\'evy stable distributions is powerful, but the
-  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
-  accuracy and computational tractability. Treating the dynamics as fractional 
-  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is well below 2.
+%  Choosing which model to use for long timescale projections is not entirely obvious
+%  without experimental data to compare with. For our comparisons to MD, using a 
+%  truncated power law distribution is an obvious choice. However, given that extremely
+%  long dwells are a rare event, it is possible that studying a much larger set of 
+%  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
+%  distributions, the generality of L\'evy stable distributions is powerful, but the
+%  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
+%  accuracy and computational tractability. Treating the dynamics as fractional 
+%  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is well below 2.
 
@@
 
-  %BJC4: maybe some kind of transitional paragraph here.
-
-  To create an MSDDM for each solute, we determined the state sequence of each 
-  solute solute trajectory and then generated emission distributions for fluctuations
+  %BJC4: added transitional paragraph
+  The AD model is useful if one does not know exact transport mechanisms 
+  in a system since it only requires time series data. However, since we have
+  already studied transport mechanisms in detail in our previous work, we can
+  attempt to model transport as transitions between known discrete
+  states, defined in Table~\ref{table:states}, with state-dependent positional
+  fluctuations, which we call the MSDDM.
+
+  % BJC4: I moved this discussion up. It used to be after I presented the parameters
+  Solute size and chemical functionality influence which states are visited most frequently.
+  In Figure~\ref{fig:state_probabilities}, we plotted the probabilities of occupying
+  a given state at any time. Urea and acetic acid spend slightly more than half 
+  their time in the tails (56\% and 62\% of their time respectively) while ethylene
+  glycol spends about 44\% of its time in the tails. Urea and acetic acid's compact
+  and flat structure allows it to more easily partition into the tails while ethylene
+  glycol prefers the pore region due to its two hydrophilic hydroxyl groups. Meanwhile
+  methanol spends 91 \% of its time in the tails likely due to its small size.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.475\textwidth]{state_probabilities.pdf}
+  \caption{Solutes spend varying amounts of time under the influence of each
+  trapping mechanism. Methanol spends the majority of its time in the tail region
+  while the rest of solute spend similar amounts of time in each region.}\label{fig:state_probabilities}
+  \end{figure}
+
+  Urea spends the largest fraction of its time trapped via association with sodium ions.
+  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
+  total time while in the pores (state 7). The electron-dense and unshielded oxygen
+  atom of urea's carbonyl group is prone to associate with positively charged sodium
+  ions. The nitrogen atoms of urea are only weak hydrogen bond donors.
+
+  Ethylene glycol spends the largest fraction of its time trapped in a hydrogen
+  bonded state. It does so 24\% of the total time while in the tails (state 2)
+  and 32\% of the total time while in the pores (state 6). The two hydroxyl groups 
+  of ethylene glycol readily donate their hydrogen atoms to the carboxylate
+  head groups and the ether linkages between the head groups and monomer tails.
+
+  Methanol spends most of its time unbound in the tail region (state 1) and spends a 
+  significant portion of time hydrogen bonded to while in the tail regions.
+  Most of the tail region hydrogen bonds are donated from methanol to the ether
+  linkages between the monomer head groups and tails.
+
+  Finally, acetic acid spends the majority of its time hydrogen bonding both in and out
+  of the pore (states 2 and 6). Although it has an unshielded carbonyl group in its
+  structure, association with sodium ions in this environment is apparently a much 
+  weaker interaction than hydrogen bonding.
+
+  To create an MSDDM for each solute, we determined the state sequence associated
+  with each solute trajectory and then generated emission distributions of fluctuations
   within each state as well as transitions between states. There are not enough 
@@
   The parameters of the L\'evy stable distributions along with their Hurst parameters 
-  are tabulated in Table~\ref{table:msddm_params}.
-
-  %MRS4: might this work better visually?  Table in SI, figure here?
+  are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated in the Supporting
+  Information, Table~\ref{S-table:msddm_params}).
+
   \begin{figure}
@@
 
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-  \hline
-  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
-  State & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$   & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$ \\\hline
-  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045      & 0.11  & 1.56     & 0.052    & 0.10 & 1.78     & 0.035    \\
-  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037      & 0.07  & 1.63     & 0.043    & 0.08 & 1.88     & 0.032    \\
-  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030      & 0.02  & 1.80     & 0.036    & 0.04 & 2.00     & 0.030    \\
-  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028      & 0.02  & 1.75     & 0.036    & 0.04 & 2.00     & 0.027    \\
-  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062      & 0.10  & 1.28     & 0.074    & 0.13 & 1.47     & 0.048    \\
-  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040      & 0.03  & 1.50     & 0.042    & 0.09 & 1.70     & 0.038    \\
-  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040      & 0.28  & 1.20     & 0.043    & 0.08 & 1.77     & 0.031    \\
-  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030      & 0.04  & 1.83     & 0.037    & 0.01 & 2.00     & 0.030    \\
-  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045      & 0.35  & 1.45     & 0.057    & 0.34 & 1.54     & 0.040    \\\hline
-  \end{tabular}
-  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
-  trajectories and used them to generate realizations of our MSDDM model. The states
-  are defined in Table~\ref{table:states} except state T which describes the transition
-  emissions.}\label{table:msddm_params}
-  \end{table}
-
-  %BJC4: better visualization scheme
   \begin{figure}
   \centering
-  \begin{subfigure}{0.49\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{H_v_state.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.49\textwidth}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
+  \caption{}\label{fig:sigma_v_state}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{alpha_v_state.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
-  \caption{}\label{fig:sigma_v_state}
-  \end{subfigure}
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{state_probabilities.pdf}
-  \caption{}\label{fig:state_probabilities}
-  \end{subfigure}
-  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
-  trajectories and used them to generate realizations of our MSDDM model. The states
-  are defined in Table~\ref{table:states} except state T which describes the transition
-  emissions.}\label{fig:msddm_parameters}
+  \caption{The parameters of the MSDDM are strong functions of trapping mechanisms.
+  We observe different parameters bu with similar trends between the tail and pore
+  region. The states are defined in Table~\ref{table:states}. To aid the reader, we 
+  labeled each state with an abbreviation which identifies the combination of 
+  conditions to which each solute is subject: t - tails, p - pores, h - hydrogen bonded, 
+  a - associated with sodium. The legend in (a) applies to all subplots. (a) Motion is
+  highly anti-correlated in trapped states. As the number of simultaneously influencing
+  trapping mechanisms increases, the Hurst parameter decreases. The Hurst parameter is
+  highest during transitions between states (state T). (b) As more trapping mechanisms
+  simultaneously influence solutes, the width of the hop length distribution decreases.
+  The largest hops occur when solutes are unbound in the pores. (c) The weight of the 
+  hop length distribution's tails, parameterized by $\alpha_h$ increases as more trapping
+  mechanisms influence solute simultaneously. The transition hop distributions have
+  among the heaviest tails.}\label{fig:msddm_parameters}
   \end{figure}
-
-%  
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
-%  \hline
-%  & \multicolumn{4}{c|}{Urea}                      & \multicolumn{4}{c|}{Ethylene Glycol} \\\hline
-%  State & H     & $\alpha_h$ & $\sigma$ & $T_{ii}$ & H    & $\alpha_h$ & $\sigma$ & $T_{ii}$  \\\hline
-%  1     & 0.10  & 1.79       & 0.034    &  0.60    & 0.09 & 1.68       & 0.045    & 0.41 \\
-%  2     & 0.06  & 1.80       & 0.033    &  0.38    & 0.09 & 1.75       & 0.037    & 0.58 \\
-%  3     & 0.11  & 1.88       & 0.030    &  0.73    & 0.11 & 1.86       & 0.030    & 0.21 \\
-%  4     & 0.10  & 1.95       & 0.027    &  0.57    & 0.04 & 1.91       & 0.028    & 0.34 \\
-%  5     & 0.19  & 1.34       & 0.048    &  0.62    & 0.15 & 1.40       & 0.062    & 0.47 \\
-%  6     & 0.15  & 1.45       & 0.040    &  0.38    & 0.11 & 1.52       & 0.040    & 0.62 \\
-%  7     & 0.15  & 1.61       & 0.032    &  0.61    & 0.05 & 1.60       & 0.040    & 0.15 \\
-%  8     & 0.11  & 1.71       & 0.028    &  0.41    & 0.05 & 1.74       & 0.030    & 0.29 \\
-%  T     & 0.34  & 1.42       & 0.036    &   --     & 0.37 & 1.44       & 0.045    &  --  \\\hline
-%  \end{tabular}
-%  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
-%  trajectories and then computed the average ensemble-averaged MSD of 10000 
-%  simulated trajectories. The states are defined in Table~\ref{table:states}
-%  except state T which refers to the transition emissions.}\label{table:msddm_params}
-%  \end{table}
-
-%  \begin{table}[h]
-%  \centering
-%  \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
-%  \hline
-%  & \multicolumn{3}{c|}{Urea}                      & \multicolumn{3}{c|}{Ethylene Glycol} \\\hline
-%  State & H     & $\alpha_h$ & $\sigma$  & H    & $\alpha_h$ & $\sigma$ \\\hline
-%  1     & 0.10  & 1.79       & 0.034     & 0.09 & 1.68       & 0.045    \\
-%  2     & 0.06  & 1.80       & 0.033     & 0.09 & 1.75       & 0.037    \\
-%  3     & 0.11  & 1.88       & 0.030     & 0.11 & 1.86       & 0.030    \\
-%  4     & 0.10  & 1.95       & 0.027     & 0.04 & 1.91       & 0.028    \\
-%  5     & 0.19  & 1.34       & 0.048     & 0.15 & 1.40       & 0.062    \\
-%  6     & 0.15  & 1.45       & 0.040     & 0.11 & 1.52       & 0.040    \\
-%  7     & 0.15  & 1.61       & 0.032     & 0.05 & 1.60       & 0.040    \\
-%  8     & 0.11  & 1.71       & 0.028     & 0.05 & 1.74       & 0.030    \\
-%  T     & 0.34  & 1.42       & 0.036     & 0.37 & 1.44       & 0.045    \\\hline
-%  \end{tabular}
-%  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
-%  trajectories and then computed the average ensemble-averaged MSD of 10000 
-%  simulated trajectories. The states are defined in Table~\ref{table:states}
-%  except state T which refers to the transition emissions.}\label{table:msddm_params}
-%  \end{table}
 
@@
   Perfectly anti-correlated motion ($H$=0) results in no contribution to the solute's
-  MSD. Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
+  MSD. There is a weak negative trend in the Hurst parameter values as the number
+  of simultaneously influencing trapping mechanisms increases (Figure~\ref{fig:H_v_state}). 
+  Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
   trapping mechanisms. Highly anti-correlated behavior in the pores in the absence of
@@
 
-  As solutes are influenced by more trapping effects simultaneously, the width of
-  the hop length distribution, $\sigma$, decreases while its L\'evy index increases.
-  Treating the tail and pore regions independently, $\sigma$ is largest and $\alpha_h$
-  is smallest when solutes are not hydrogen bonding or associating with sodium (states 1 and 5).
-  Solutes are free to move and take occasionally large hops. The smallest $\sigma$
-  and highest $\alpha_h$ values are measured when solutes are hydrogen bonding and 
-  associating with sodium at the same time (states 4 and 8). Motion is restricted 
-  by multiple tethers which maintains a relatively narrow distribution of hop lengths.
-
-  The trapping mechanisms affect each solute to varying degrees. The probabilities
-  of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
-  Urea and acetic acid spend slightly more than half their time in the tails (56\% and 62\% 
-  of their time respectively) while ethylene glycol spends about 44\% of its time in the tails.
-  Urea and acetic acid's compact and flat structure allows it to more easily 
-  partition into the tails while ethylene glycol prefers the pore region due to 
-  its two hydrophilic hydroxyl groups. Meanwhile methanol spends 91 \% of its 
-  time in the tails likely due to its small size.
-
-  %MRS4: make it more clear you are still taking about trapping mechanisms here.
-  Urea spends the largest fraction of its time trapped via association with sodium ions.
-  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
-  total time while in the pores (state 7). The electron-dense and unshielded oxygen
-  atom of urea's carbonyl group is prone to associate with positively charged sodium
-  ions. The nitrogen atoms of urea are only weak hydrogen bond donors.
-
-  Ethylene glycol spends the largest fraction of its time trapped in a hydrogen
-  bonded state. It does so 24\% of the total time while in the tails (state 2)
-  and 32\% of the total time while in the pores (state 6). The two hydroxyl groups 
-  of ethylene glycol readily donate their hydrogen atoms to the carboxylate
-  head groups and the ether linkages between the head groups and monomer tails.
-
-  Methanol spends most of its time unbound in the tail region (state 1) and spends a 
-  significant portion of time hydrogen bonded to while in the tail regions.
-  Most of the tail region hydrogen bonds are donated from methanol to the ether
-  linkages between the monomer head groups and tails.
-
-  Finally, acetic acid spends the majority of it's time hydrogen bonding in and out
-  of the pore.
-
-  % /figures/msddm_state_probabilities.py
-  %BJC4: combined with previous figure.
-%  \begin{figure}
-%  \centering
-%  \includegraphics[width=0.5\textwidth]{state_probabilities.pdf}
-%  \caption{The probability of finding urea or ethylene glycol in a given state.}\label{fig:state_probabilities}
-%  \end{figure}
-%
-
-  %BJC3: show how much of the MSD comes from each? Not sure this will work because of transition matrix dependence
-  %BJC3: can just say
-
-  % BJC2: This figure will show predicted MSDs versus MD MSDs
+  As solutes are influenced by more trapping interactions simultaneously (i.e. hydrogen
+  bonding \textit{and} associated with sodium versus just hydrogen bonding), the 
+  width of the hop length distribution, $\sigma$, decreases while its L\'evy index,
+  $\alpha_h$, increases. Treating the tail and pore regions independently, $\sigma$
+  is largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding or 
+  associating with sodium (states 1 and 5). Solutes are free to move and take 
+  occasionally large hops. The smallest $\sigma$ and highest $\alpha_h$ values are
+  measured when solutes are hydrogen bonding and associating with sodium at the
+  same time (states 4 and 8). Motion is restricted by multiple tethers which 
+  maintains a relatively narrow distribution of hop lengths.
+
+%  The trapping mechanisms affect each solute to varying degrees. The probabilities
+%  of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
+%  Urea and acetic acid spend slightly more than half their time in the tails (56\% and 62\% 
+%  of their time respectively) while ethylene glycol spends about 44\% of its time in the tails.
+%  Urea and acetic acid's compact and flat structure allows it to more easily 
+%  partition into the tails while ethylene glycol prefers the pore region due to 
+%  its two hydrophilic hydroxyl groups. Meanwhile methanol spends 91 \% of its 
+%  time in the tails likely due to its small size.
+
+  Using the parameters shown in Figure~\ref{fig:msddm_parameters}, we simulated 
+  1000 MSDDM trajectory realizations as described in Section~\ref{method:MSMs}
+  then calculated their MSDs. The MSDDM over-estimates solute MSDs by c.a. 250--650 \%
+  (see Figure~\ref{fig:msddm_performance}).
+
   \begin{figure}
@@
   \includegraphics[width=\textwidth]{ACH_msddm.pdf}
-  \caption{}\label{fig:ACH_msddm}
-  \end{subfigure}
-  \caption{MSDs predicted by the MSDDM significantly over-predict those
-  from generated from MD simulations.}\label{fig:msddm_performance}
+  \caption{Acetic Acid}\label{fig:ACH_msddm}
+  \end{subfigure}
+  \caption{The MSD curves predicted by the MSDDM significantly over-predict the
+  magnitude and misrepresent the curvature of those generated from MD simulations.
+  We expect urea and acetic acid to show some curvature on these time scales.}\label{fig:msddm_performance}
   \end{figure}
 
-  %BJC3: would take ~ 20 hours to simulation 10000 trajectories.
-  %MRS4: state how much it overestimated (1% or 10000%?)
-  %BJC4: added percentages. Is it redundant since I already said how many time
-  The MSDDM over-estimates solute MSDs by 200--300 \% (see Figure~\ref{fig:msddm_performance}). 
-  We simulated 1000 trajectories as described in Section~\ref{method:MSMs} then
-  %BJC3: 2.2 and 3.3 x higher than MD to be exact
-  calculated their MSDs. The MSDs of urea and ethylene glycol are about 2 and 3 times
-  higher than MD simulations respectively.
-
-  %MRS4: It's not as clear what effect you are talking about until
-  %later, i.e. the fact that the correlation is destroyed by the
-  %state switching.
-  %BJC4: modified thesis
-  The MSDDM overestimates solute MSDs because correlation is lost
-  every time a state switch occurs. Although correlation exists within each
-  sequence, there is no memory of the previous state or state transition 
-  that can be built into the first emission of the most recent state. 
-  This implies that the first value in a state sequence is a random
-  draw from the underlying emission distribution. Frequent transitions
-  between states lead to an abundance of short dwell times. It is 
-  difficult to accurately correlate short sequences so we are 
-  almost simulating uncorrelated draws from the emission distribution.
-  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying 
-  the transition matrix and simulating a simple 2-state model with parameters
-  similar to those in Table~\ref{table:msddm_params} (see Table~\ref{S-table:msddm_params}
-  of the Supporting Information). We modified the probability
-  transition matrix, $T$, in order to control the probability of 
-  self-transitions (the diagonal elements of $T$). Larger self-transition probabilities lead to longer dwell 
-  times in each state. We set the off-diagonal elements of $T$ to be equal values that make the
-  rows of $T$ sum to unity when combined with the self-transition probabilities. 
-  As we increase the self-transition probability, $T_{ii}$, the simulated MSD 
-  decreases. Consequently longer dwell times in each state allow us to more accurately
-  simulate the negative correlation that we observe in MD.
+  %It is clear that the predictive
+  %abilities of the MSDDM are inadequate but it is still possible to salvage
+  %key insights.
+
+  The MSDDM overestimates solute MSDs because correlation is lost every time a
+  state switch occurs. Although correlation exists within each sequence, there
+  is no memory of the previous state or state transition that can be built into
+  the first emission of the most recent state. This implies that the first 
+  value in a state sequence is a random draw from the underlying emission 
+  distribution. Frequent transitions between states lead to an abundance of 
+  short dwell times. It is difficult to accurately correlate short sequences so
+  we are almost simulating uncorrelated draws from the emission distribution.
+  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying the
+  transition matrix and simulating a simple 2-state model with parameters similar
+  to those in Table~\ref{table:msddm_params} (we tabulated the parameters used 
+  in Table~\ref{S-table:msddm_params} of the Supporting Information). We modified
+  the probability transition matrix, $T$, in order to control the probability of 
+  self-transitions (the diagonal elements of $T$). Larger self-transition 
+  probabilities lead to longer dwell times in each state. We set the off-diagonal
+  elements of $T$ to be equal values that make the rows of $T$ sum to unity when
+  combined with the self-transition probabilities. As we increase the 
+  self-transition probability, $T_{ii}$, the simulated MSD decreases. Consequently,
+  longer dwell times in each state allow us to more accurately simulate the
+  negative correlation that we observe in MD.
 

### 2019-12-11 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Adjusting visualizations
New figures and analysis to paper. Parallelization to scripts

@@
 \usepackage{xr}
+\usepackage{array}
+\usepackage{multirow}
+\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
+\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
+\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
+\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
+\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
+\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
 
@@
 
+  \section{Solute hopping and trapping behavior}\label{section:sfbm_other_solutes}
+
+  \begin{figure}
+  \centering
+  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
+  % /figures/solute_trajectories.py
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
+  \caption{}\label{fig:GCL_solute_trajectories}
+  \end{subfigure}
+  % Next 3: /figures/distributions_sfbm.py
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
+  \caption{}\label{fig:GCL_hop_distribution_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
+  \caption{}\label{fig:GCL_powerlaw}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
+  \caption{}\label{fig:GCL_hop_acf}
+  \end{subfigure}
+  \caption{For ethylene glycol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
+  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
+  for ethylene glycol. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
+  in the main text for a more detailed discussion.}\label{fig:GCL_anticorrelated_hops}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
+  % /figures/solute_trajectories.py
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
+  \caption{}\label{fig:ACH_solute_trajectories}
+  \end{subfigure}
+  % Next 3: /figures/distributions_sfbm.py
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
+  \caption{}\label{fig:ACH_hop_distribution_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
+  \caption{}\label{fig:ACH_powerlaw}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
+  \caption{}\label{fig:ACH_hop_acf}
+  \end{subfigure}
+  \caption{For acetic acid: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
+  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
+  for acetic acid. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
+  in the main text for a more detailed discussion.}\label{fig:ACH_anticorrelated_hops}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
+  % /figures/solute_trajectories.py
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{MET_trajectories.pdf}
+  \caption{}\label{fig:MET_solute_trajectories}
+  \end{subfigure}
+  % Next 3: /figures/distributions_sfbm.py
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
+  \caption{}\label{fig:MET_hop_distribution_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
+  \caption{}\label{fig:MET_powerlaw}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
+  \caption{}\label{fig:MET_hop_acf}
+  \end{subfigure}
+  \caption{For methanol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
+  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
+  for methanol. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
+  in the main text for a more detailed discussion.}\label{fig:MET_anticorrelated_hops}
+  \end{figure}
+
+  \section{Tabular Anomalous Diffusion Parameters}\label{section:tabular_AD_params}
+
+  % BJC: note to self -- modes are flipped in simulation output because 
+  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
+  \hline
+  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
+  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
+  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
+  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
+  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
+  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
+  \hline 
+  \end{tabular}
+  \caption{To create a 1 mode model for each solute, we parameterized a pure power
+  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
+  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
+  law tails and higher values of $\lambda$ truncate the distribution at lower
+  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
+  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
+  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
+  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
+  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
+  function ($\gamma(H)$) to describe the degree of correlation between hops. 
+  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
+  \end{table}
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
+  \hline
+  \multicolumn{7}{|c|}{2 Mode Model} \\\hline
+                & Parameters                               & Mode & Urea         & Ethylene Glycol &  Methanol    & Acetic Acid \\
+  \hline
+                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.90         & 0.58         \\\cline{3-7}
+  Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
+  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.04, 0.0006 & 0.41, 0.0026 \\\cline{3-7}
+                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.30, 0.0054 & 0.00, 0.0021 \\\hline
+                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.45         & 0.32         \\\cline{3-7}
+  Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
+  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.31, 1.97   & 0.21, 1.91   \\\cline{3-7}
+                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.85   & 0.09, 1.50   \\\hline
+  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
+  \hline 
+  \end{tabular}
+  \caption{The two model parameterizes solute behavior in the pores and tails separately. 
+  Generally, movement is much more restricted in the tail region. To create a 2 mode model,
+  we generated a set of parameters based on solute behavior as function of distance from
+  the pore center. Mode 1 corresponds to solute behavior within 0.75 nm of the pore center
+  and mode 2 corresponds to behavior greater than or equal to 0.75 nm from the pore center.
+  Note that we used the same Hurst parameter for both modes due to a low number of 
+  sufficiently long sequences of hops in each mode. See Table~\ref{table:sfbm_params} for
+  descriptions of the parameters.}\label{table:sfbm_params_2mode}
+  \end{table}
+
   \section{Stationarity of Solute Trajectories}\label{section:msd_comparison}
@@
 
+  \section{Tabular MSDDM parameters}\label{section:msddm_params}
+
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+  \hline
+  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
+  State & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$   & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$ \\\hline
+  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045      & 0.11  & 1.56     & 0.052    & 0.10 & 1.78     & 0.035    \\
+  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037      & 0.07  & 1.63     & 0.043    & 0.08 & 1.88     & 0.032    \\
+  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030      & 0.02  & 1.80     & 0.036    & 0.04 & 2.00     & 0.030    \\
+  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028      & 0.02  & 1.75     & 0.036    & 0.04 & 2.00     & 0.027    \\
+  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062      & 0.10  & 1.28     & 0.074    & 0.13 & 1.47     & 0.048    \\
+  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040      & 0.03  & 1.50     & 0.042    & 0.09 & 1.70     & 0.038    \\
+  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040      & 0.28  & 1.20     & 0.043    & 0.08 & 1.77     & 0.031    \\
+  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030      & 0.04  & 1.83     & 0.037    & 0.01 & 2.00     & 0.030    \\
+  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045      & 0.35  & 1.45     & 0.057    & 0.34 & 1.54     & 0.040    \\\hline
+  \end{tabular}
+  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
+  trajectories and used them to generate realizations of our MSDDM model. The states
+  are defined in Table~\ref{table:states} except state T which describes the transition
+  emissions.}\label{table:msddm_params}
+  \end{table}
+
   \section{2-state MSDDM parameters}\label{section:simple_msddm_params}
@@
 
-  We validated our approach to simulating trajectory realizations by testing
-  it against analytical solutions to the mean first passage time of a Brownian
-  particle with 2 absorbing boundaries.
+%  We validated our approach to simulating trajectory realizations by testing
+%  it against analytical solutions to the mean first passage time of a Brownian
+%  particle with 2 absorbing boundaries.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{mfpt_curves_brownian.pdf}
+  \caption{}\label{fig:mfpt_curve_brownian}
+  \end{figure}
 

### 2019-12-12 Ben_Manuscripts/stochastic_transport/Draft.tex
Added comments on flux sections.

@@
   where $J$ is the single particle solute flux and MFPT refers to the mean first passage
-  time. For particle concentrations higher than 1 at the pore entrance, one can multiply
+  time. 
+  %MRS5: I would phrase below: 
+  To account for input concentration dependence of the flux, assuming that 
+  particles are uncorrelated, 
+  %For particle concentrations higher than 1 at the pore entrance, 
+  one can multiply
   Equation~\ref{eqn:hill_relation} by the total number of particles to get the total flux.
@@
   a function of time. 
-
+  %MRS5: I would put this next section up until just before Eq. 15 in the supporting information (keep any citations in the main text). 
   To derive an analytical equation, first consider an initial pulse spreading out 
@@
   \begin{equation}
-  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-z^2}{4Dt}\bigg)
+  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
   \end{equation}
@@
   \begin{equation}
-  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
+  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
   \end{equation}
@@
   \begin{equation}
-  F(t) = \int_L^\infty p~dz = erfc\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
+  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
   \end{equation}
@@
 
+  %MRS5: One question is if other method would lead to substantially
+  %different results for fluxes or selectivity.  May need too think
+  %about justification more if just one method is mentioned.
+
+  %MRS5: I think it might be useful to have at least visualizions of
+  %distribution of FPT and its fit.  It might not be obvious to
+  %readers that the different mechanisms have distributions of FPT
+  %that are well decscribed by the relatively simple moving diffusion
+  %equation in eq 15.
+
+  %Does't fitting to eq 15 cut down on the expense of the number of trajectories
+  %by a fair amount?  Should there be some discussion of this?
+
   %BJC4: not sure if the next couple paragraphs belong in methods 
-  It is computationally unfeasible to simulate trajectories long enough that they
+  %MRS5: this could potentially be in methods.  Alternatives can be discussed there.
+  It is computationally infeasible to simulate trajectories long enough that they
   traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
@@
   RAM requirements and performance scales greater than linearly and thus would 
-  take an unfeasible amount of memory and time to simulate transport through a 
+  take an infeasible amount of memory and time to simulate transport through a 
   pore over 100 times longer.
@@
   %BJC4: methods?  
+  %MRS5: This requires knowing the data, so maybe here. 
   We used simulated trajectories which traverse computationally-reasonable length
@@
 
+  %MRS: can you put a physical thesis here, not just a mathematical one?  Why is this change in parameters important to flux?
   The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
@@
 
+  %MRS5: probably the figure showing beta \sim 2 can be in supporting
+  %information, and you just state the result here.
+
   Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
@@
   hops made by methanol outweighs its relatively wide hop length distribution.
+
+%MRS: can you connect directly to $\beta$ and $c$ here?  Important to
+%make connections between macroscopic parameters and the molecular
+%reason for them whenever possible.  Can combine with other paragraphs that talk mainly about c and beta.
 
@@
 %  \end{subfigure}
+  %MRS5: the b) pane is a little messy.  If c) is moved to the supporting, maybe can make b into two figures, and 
+  % have each just show 1 point? 
   \caption{(a) The single particle solute flux decays with increasing pore length. 
@@
   correlation between hops (set $H$=0.5), the flux increases significantly and 
-  $\beta$ is constant at about 2 for all solutes independent of dwell distribution
+  $\beta \sim 2$ for all solutes independent of dwell distribution
   parameters.}\label{fig:flux_curves}
@@
 
+  %MRS5: figure seem to show that the selectivity plateaus more or less, so thin coatings enough. 
   In Figure~\ref{fig:selectivity}, we plot Equation~\ref{eqn:selectivity_ratio} for pore
@@
   depends on the pre-factors, $c$. 
+  %MRS5?
+can you remind people of the physical source (in terms of dwell times, hop lengths) of the differences in beta and c?
+Want to try to stablish the connection between particle dynamic behavior and selectivity.
 
@@
   Out of the solutes studied, the data suggests that this particular LLC membrane 
-  would be most useful for selectively separating ethylene glycol from methanol and 
+  %MRS5: would is a bit strong given the number of limitations.
+  %would 
+  might
+  be most useful for selectively separating ethylene glycol from methanol and 
   acetic acid. 
@@
 
+  %MRS5: sentence fragment left here?
     Neglects concentration polarization, membrane defects and fouling.

### 2019-12-12 Ben_Manuscripts/stochastic_transport/Draft.tex
Figure updates

@@
   where $J$ is the single particle solute flux and MFPT refers to the mean first passage
-  time. 
-  %MRS5: I would phrase below: 
-  To account for input concentration dependence of the flux, assuming that 
-  particles are uncorrelated, 
-  %For particle concentrations higher than 1 at the pore entrance, 
-  one can multiply
-  Equation~\ref{eqn:hill_relation} by the total number of particles to get the total flux.
-  In the context of our work, the MFPT describes the average length of time it takes a particle
-  to move from the pore entrance to the pore exit.
+  time. To account for input concentration dependence of the flux, assuming that particles
+  are uncorrelated, one can multiply Equation~\ref{eqn:hill_relation} by the total number
+  of particles to get the total flux. In the context of our work, the MFPT describes the
+  average length of time it takes a particle to move from the pore entrance to the pore exit.
 
@@
   one can frame the problem as a pulse of particles instantaneously released at the 
-  pore inlet ($z=0$) which moves at a constant velocity and spreads out as it 
-  approaches $L$. This gives results equivalent to if we had released each particle
-  individually and then analyzed the positions of the ensemble of trajectories as 
-  a function of time. 
-  %MRS5: I would put this next section up until just before Eq. 15 in the supporting information (keep any citations in the main text). 
-  To derive an analytical equation, first consider an initial pulse spreading out 
-  over time with a fixed mean. We can solve for the time-dependent probability density
-  of particle positions by solving the one dimensional diffusion equation:
-  \begin{equation}
-  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
-  \end{equation}
-  The appropriate initial and boundary conditions are:
-  $$BC1: t > 0, z = \infty, p = 0$$
-  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
-  $$IC: t = 0, c = M\delta(z)$$
-  where $M$ is the total number of particles in the system. It has been shown 
-  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
-  \begin{equation}
-  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
-  \end{equation}
-  We can make the substitution $z = z - vt$, where $v$ represents a constant average
-  velocity, in order to linearly shift the mean as a function of time:
-  \begin{equation}
-  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
-  \end{equation}
-  One can track the fraction of particles, $F$, that have crossed the pore 
-  boundary by integrating:
-  \begin{equation}
-  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
-  \end{equation}
-  where $L$ is the pore length. This represents the cumulative first passage 
-  time distribution so we take its derivative in order to arrive at the first
-  passage time distribution:
+  pore inlet ($z=0$) which moves at a constant velocity, $v$, and spreads out as it 
+  approaches $L$. This spreading is parameterized by an effective diffusivity 
+  parameter, $D$. This approach gives results equivalent to if we had released each
+  particle individually and then analyzed the positions of the ensemble of trajectories as 
+  a function of time. The analytical expression describing the distribution of 
+  first passage times is:~\cite{cussler_diffusion:_2009}
   \begin{equation}
@@
   \end{equation} 
-  where the only free parameters for fitting are $v$ and $D$. We calculated the
-  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT.
+  where the only free parameters for fitting are $v$ and $D$. A derivation
+  of Equation~\ref{eqn:passage_times} is given in Section~\ref{S-section:fpt_derivation}
+  of the Supporting Information. We calculated the expected value of 
+  Equation~\ref{eqn:passage_times} in order to get the MFPT.
+
+  %MRS5: I would put this next section up until just before Eq. 15 in the supporting information (keep any citations in the main text). 
+  %BJC5: moved to supporting
+%  To derive an analytical equation, first consider an initial pulse spreading out 
+%  over time with a fixed mean. We can solve for the time-dependent probability density
+%  of particle positions by solving the one dimensional diffusion equation:
+%  \begin{equation}
+%  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
+%  \end{equation}
+%  The appropriate initial and boundary conditions are:
+%  $$BC1: t > 0, z = \infty, p = 0$$
+%  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
+%  $$IC: t = 0, c = M\delta(z)$$
+%  where $M$ is the total number of particles in the system. It has been shown 
+%  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
+%  \begin{equation}
+%  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
+%  \end{equation}
+%  We can make the substitution $z = z - vt$, where $v$ represents a constant average
+%  velocity, in order to linearly shift the mean as a function of time:
+%  \begin{equation}
+%  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
+%  \end{equation}
+%  One can track the fraction of particles, $F$, that have crossed the pore 
+%  boundary by integrating:
+%  \begin{equation}
+%  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
+%  \end{equation}
+%  where $L$ is the pore length. This represents the cumulative first passage 
+%  time distribution so we take its derivative in order to arrive at the first
+%  passage time distribution:
 
@@
   We can relate this to solute flux using Kedem and Katchalsky's equations for 
-  solvent volumetric flux, $J_v$, and solute flux, $J_s$:~\cite{kedem_permeability_1963}
+  solvent volumetric flux, $J_v$, and solute flux, $J_s$:~\cite{kedem_permeability_1963,al-zoubi_rejection_2007}
   %al-zoubi_rejection_2007 clarifies that these equations can be used for nanofiltration, ultrafiltration etc. by treating the membrane as a black box subject to irreversible thermodynamics.
@@
   %MRS5: this could potentially be in methods.  Alternatives can be discussed there.
+  %BJC5: I tried putting this in methods, but it feels weird without stating the
+  % empirical equation. And I'm avoiding stating the empirical model in the methods
+  % since it is informed by the data.
   It is computationally infeasible to simulate trajectories long enough that they
@@
 
-  %BJC4: methods?  
-  %MRS5: This requires knowing the data, so maybe here. 
   We used simulated trajectories which traverse computationally-reasonable length
@@
   \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{flux_parameters.pdf}
-  \caption{}\label{fig:flux_parameters}
+  \includegraphics[width=\textwidth]{c_parameters.pdf}
+  \caption{}\label{fig:c_parameters}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{beta_parameters.pdf}
+  \caption{}\label{fig:beta_parameters}
   \end{subfigure}
@@
   %BJC: might get closer to beta=2 if I use different curve fitting technique than fitting line to log-log
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
-  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
-  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
+%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
+%  \end{subfigure}
 %  \begin{subfigure}{0.475\textwidth}
@@
   LLC membrane made from a specific monomer.
-  %BJC: though about mentioning fouli
-
-  %MRS5: sentence fragment left here?
-    Neglects concentration polarization, membrane defects and fouling.
 

### 2019-12-12 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Figure updates

@@
 
+  \section{Derivation of Passage Time Distributions}\label{section:fpt_derivation}
+
+  To derive an analytical equation for the mean first passage time as calculated
+  in the main text, first consider an initial pulse spreading out over time with
+  a fixed mean. We can solve for the time-dependent probability density of 
+  particle positions by solving the one dimensional diffusion equation:
+  \begin{equation}
+  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
+  \end{equation}
+  The appropriate initial and boundary conditions are:
+  $$BC1: t > 0, z = \infty, p = 0$$
+  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
+  $$IC: t = 0, c = M\delta(z)$$
+  where $M$ is the total number of particles in the system. It has been shown 
+  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
+  \begin{equation}
+  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
+  \end{equation}
+  We can make the substitution $z = z - vt$, where $v$ represents a constant average
+  velocity, in order to linearly shift the mean as a function of time:
+  \begin{equation}
+  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
+  \end{equation}
+  One can track the fraction of particles, $F$, that have crossed the pore 
+  boundary by integrating:
+  \begin{equation}
+  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
+  \end{equation}
+  where $L$ is the pore length. This represents the cumulative first passage 
+  time distribution so we take its derivative in order to arrive at the first
+  passage time distribution:
+  \begin{equation}
+  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
+  \label{eqn:passage_times}
+  \end{equation} 
+  where the only free parameters for fitting are $v$ and $D$. We calculated the
+  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT.
+
   \section{Solute hopping and trapping behavior}\label{section:sfbm_other_solutes}
@@
   \begin{figure}
+  \includegraphics[width=0.5\textwidth]{flux_curves_brownian.pdf}
+  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
+  \end{figure}
+
+  \begin{figure}
   \centering

### 2019-12-12 LLC_Membranes/analysis/markov_state_dependent_dynamics.py

@@ -683,7 +683,7 @@ class Chain:
 
             # unpack result list
             for i, r in enumerate(result):
-                
+
                 self.chains[:, i * trajectories_per_thread:(i + 1) * trajectories_per_thread] = r[0]
                 self.states[:, i * trajectories_per_thread:(i + 1) * trajectories_per_thread] = r[1]
 

### 2019-12-13 Ben_Manuscripts/stochastic_transport/Draft.tex
New figures + speed improvements

@@
   order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
-  parameters extracted from MD simulations. We believe the 1-mode sFBMcut model
-  shows the most promising predictive ability of the models studied in this work. 
-  %Any approach which allows one to 
-  %generate realizations of solute trajectories can be used in place of the AD model.
-
+  parameters extracted from MD simulations. The sFLMcut model and MSDDM yield 
+  similar predictions at a much greater computational cost due to the slow
+  generation of fractional L\'evy noise.
   %MRS5: One question is if other method would lead to substantially
@@
   %about justification more if just one method is mentioned.
+  %BJC5: would love to test MSDDM against this but I don't know how to make 
+  % the algorithm faster. It already uses an FFT to correlate the data (to which I pass powers of 2)
 
@@
   %equation in eq 15. 
-
-  %Does't fitting to eq 15 cut down on the expense of the number of trajectories
-  %by a fair amount?  Should there be some discussion of this?
+  %BJC5: added to figure
 
@@
   24 cores to simulate trajectory realizations in parallel, it takes on the order 
-  of 1 day to simulate 50000 realizations of solutes traversing a 50 nm pore. The 
+  of 1 day to simulate 10000 realizations of solutes traversing a 50 nm pore. The 
   RAM requirements and performance scales greater than linearly and thus would 
@@
   pores in order to construct an empirical model which one can use to estimate 
-  particle flux for arbitrary length pores. As shown in Figure~\ref{fig:flux_curves},
+  particle flux for arbitrary length pores. We fit Equation~\ref{eqn:passage_times}
+  to the empirical distribution of first passage times in Figure~\ref{fig:fpt_distributions}
+  and used the expected value of the analytical equation to calculate flux from 
+  Equation~\ref{eqn:hill_relation}. As shown in Figure~\ref{fig:flux_curves}, 
   the flux appears to scale according to a power law of the form:
@@
 
-  %MRS: can you put a physical thesis here, not just a mathematical one?  Why is this change in parameters important to flux?
-  The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
-  solute MSD while the value of the growth exponent, $\beta$, is inversely 
-  related to the Hurst parameter, $H$ (see Figure~\ref{fig:flux_parameters}).
-  In Figure~\ref{fig:flux_curves_brownian}, we removed the correlation 
-  structure (set $H$=0.5) from AD trajectory realizations so that all hops 
-  were uncorrelated. Regardless of the parameters of the dwell time distribution,
-  the growth exponent is always about 2, the same value that we observe for 
-  Brownian motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the 
-  Supporting Information).
-
-  %MRS5: probably the figure showing beta \sim 2 can be in supporting
-  %information, and you just state the result here.
-
-  Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
-  highlights that anti-correlation between hops plays a major role in solute flux.
-  With a pore length of 50 nm, the flux of the fasted moving solute, ethylene glycol is 
-  c.a. 5 times lower with versus without anti-correlated hops. The flux of the slowest
-  moving solute, acetic acid, is about 16 times lower by the same comparison. This 
-  difference will only grow with increasing pore length. Note also that the ranking
-  of solute fluxes changes. Methanol jumps from the second lowest to the highest
-  flux when we remove hop correlation. The high degree of anti-correlation among
-  hops made by methanol outweighs its relatively wide hop length distribution.
-
-%MRS: can you connect directly to $\beta$ and $c$ here?  Important to
-%make connections between macroscopic parameters and the molecular
-%reason for them whenever possible.  Can combine with other paragraphs that talk mainly about c and beta.
-
-%   In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
-%  with pore length. We fit a curve of the form  to the curves in order
-%  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
-%  to the solute MSDs which is consistent with longer passage times for solutes that
-%  progress through the pores more slowly.
-
   %BJC: need simulations with increased length for L=35-50 nm pores of acetic acid and methanol
   %BJC: see of clauset has better way of fitting t^-alpha (alpha might be too big)
-  %BJC: not sure mfpt is necessary. Takes up space.
-  %BJC: change alpha to beta
-  %BJC: make a chart with parameters
   %BJC: should have a paragraph about c -- roughly follows their MSDs.
@@
   \centering
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.475\textwidth}
+  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
+  \caption{}\label{fig:fpt_distributions}
+  \end{subfigure}
+  \begin{subfigure}{0.475\textwidth}
   \includegraphics[width=\textwidth]{flux_curves.pdf}
-  \caption{Fits to $cL^{-\beta}$}\label{fig:flux_curves_regular}
+  \caption{}\label{fig:flux_curves_regular}
   \end{subfigure}
   % BJC: could use better color scheme. Maybe outline hurst parameters
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.475\textwidth}
   \includegraphics[width=\textwidth]{c_parameters.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.475\textwidth}
   \includegraphics[width=\textwidth]{beta_parameters.pdf}
@@
 
+  %MRS5: Does't fitting to eq 15 cut down on the expense of the number of trajectories
+  %by a fair amount?  Should there be some discussion of this? 
+  %BJC5: added this
+  Although we used 10000 trajectory realizations in order to generate 
+  Figure~\ref{fig:flux_curves}, one may actually need considerably less realizations
+  in order to predict and compare flux between solutes. In Figure~\ref{S-fig:flux_curve_sensitivity}
+  of the Supporting information, we show that one can still show statistically
+  significant differences in solute flux with as little as 100 trajectory 
+  realizations.
+
+  %MRS: can you put a physical thesis here, not just a mathematical one?  Why is this change in parameters important to flux?
+  The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
+  solute MSD while the value of the growth exponent, $\beta$, is inversely 
+  related to the Hurst parameter, $H$ (see Figure~\ref{fig:flux_parameters}).
+  In Figure~\ref{fig:flux_curves_brownian}, we removed the correlation 
+  structure (set $H$=0.5) from AD trajectory realizations so that all hops 
+  were uncorrelated. Regardless of the parameters of the dwell time distribution,
+  the growth exponent is always about 2, the same value that we observe for 
+  Brownian motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the 
+  Supporting Information).
+
+  %MRS5: probably the figure showing beta \sim 2 can be in supporting
+  %information, and you just state the result here.
+
+  Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
+  highlights that anti-correlation between hops plays a major role in solute flux.
+  With a pore length of 50 nm, the flux of the fasted moving solute, ethylene glycol is 
+  c.a. 5 times lower with versus without anti-correlated hops. The flux of the slowest
+  moving solute, acetic acid, is about 16 times lower by the same comparison. This 
+  difference will only grow with increasing pore length. Note also that the ranking
+  of solute fluxes changes. Methanol jumps from the second lowest to the highest
+  flux when we remove hop correlation. The high degree of anti-correlation among
+  hops made by methanol outweighs its relatively wide hop length distribution.
+
+%MRS: can you connect directly to $\beta$ and $c$ here?  Important to
+%make connections between macroscopic parameters and the molecular
+%reason for them whenever possible.  Can combine with other paragraphs that talk mainly about c and beta.
+
+%   In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
+%  with pore length. We fit a curve of the form  to the curves in order
+%  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
+%  to the solute MSDs which is consistent with longer passage times for solutes that
+%  progress through the pores more slowly.
+
   % Partially in methods?

### 2019-12-13 Ben_Manuscripts/stochastic_transport/Draft.tex
Incorporated MSDDM into MFPT calculations

@@
   when the dwell time distributions are parameterized by a power law with an 
-  exponential cut-off. Without truncation of the power law distribution, the MD 
+  exponential cut-off. At long timescales, the MSD of Urea is under-predicted 
+  for both the 1 and 2 mode models with the same true of acetic acid on short 
+  timescales. Without truncation of the power law distribution, the MD 
   MSDs are underestimated in all cases because dwell times on the order of the
@@
   solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
+  Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
+  intervals of the MD MSD curves, they appear to lie systematically below the mean. 
+  It is not clear whether this is a consistent feature of the AD model since we 
+  only used 2 solutes for this analysis.
 
@@
   From a qualitative perspective, the models only have moderate success at predicting
-  the shape of the MSD curves. In general, the MSDs generated by our AD models appear
-  close to linear at long time scales. This is expected behavior for time averaged 
-  MSDs, especially when truncating the power law distribution of dwell times.
-  \cite{molina-garcia_crossover_2018} The linearity of Urea's MD MSD curve is 
-  consistent with that of the AD model, but the MD MSD of acetic acid appears to have considerable
-  curvature. Acetic acid's MSD is under-predicted at short timescales but within error 
-  of MD (using sFBMcut and sFLMcut models) after a 500 ns time lag. The curvature suggests that the 
-  model under-estimates long timescale positional anti-correlation which points to an
-  over-estimate of the Hurst parameter. This is not surprising because the Hurst 
-  parameter is challenging to quantify, especially with a relatively small amount of 
-  data (see Section~\ref{method:sfbm} for further discussion of this challenge).
-  A more accurate measurement of $H$ would fix the shape of the MSD curve, but also
-  lower the predicted MSD meaning we are either underestimating the width of the hop
-  length distribution, favoring longer dwell times or both.
+  the shape of the MSD curves. Error in the MSD curvature can help explain some of
+  the error in the predicted MSD magnitudes. The curves predicted for Urea with both 1 
+  and 2 modes appear to have too much curvature, which causes it to under-predict the 
+  MSD at long timescales, while those of acetic acid lack curvature, leading the
+  AD model to under-predict the MSD at short timescales.
+
+  The under-estimate of Urea's MSD at long timescales is due to long timescale
+  positional anti-correlation which may not be present in the real system. The 
+  persistent curvature of the predicted MSD curves is a direct consequence of 
+  the Hurst parameter. Without anti-correlation, the process would be 
+  a pure CTRW for which one would expect the time averaged MSD curves to become 
+  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
+  positional correlation is lost which would manifest as a transition from a sub-linear
+  to linear MSD curve. A solution for more accurately modeling this behavior in  
+  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}
+
+  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
+  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
+  because the Hurst parameter is challenging to quantify, especially with a relatively 
+  small amount of data (see Section~\ref{method:sfbm} for further discussion of this 
+  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
+  but also lower the predicted MSD meaning we are either underestimating the width of
+  the hop length distribution, favoring longer dwell times or both.
+
+%  Urea's curves appear to have
+%  close to the right amount of curvature at short timescales
+
+%  In general, the MSDs generated by our AD models appear
+%  close to linear at long time scales. This is expected behavior for time averaged 
+%  MSDs, especially when truncating the power law distribution of dwell times.
+%  \cite{molina-garcia_crossover_2018} The linearity of Urea's MD MSD curve is 
+%  consistent with that of the AD model, but the MD MSD of acetic acid appears to have considerable
+%  curvature.
+
+%  Acetic acid's MSD is under-predicted at short timescales but within error 
+%  of MD (using sFBMcut and sFLMcut models) after a 500 ns time lag. The curvature suggests that the 
+%  model under-estimates long timescale positional anti-correlation which points to an
+%  over-estimate of the Hurst parameter. This is not surprising because the Hurst 
+%  parameter is challenging to quantify, especially with a relatively small amount of 
+%  data (see Section~\ref{method:sfbm} for further discussion of this challenge).
+%  A more accurate measurement of $H$ would fix the shape of the MSD curve, but also
+%  lower the predicted MSD meaning we are either underestimating the width of the hop
+%  length distribution, favoring longer dwell times or both.
   % BJC4: play around with this to see how to change shape of acetic acid curve. Hurst makes it arc more
@@
 
-  This brief analysis suggests that working with only half of the data we collected
+  This brief analysis suggests two shortcomings of the AD model. First, positional
+  anti-correlation may diminish after a sufficiently long time lag, dependent on the 
+  solute being studied. Second, it is difficult to reliably parameterize the Hurst
+  parameter which is important for accurately describing the curvature of the solute
+  MSDs.
+
+  This analysis also suggests that working with only half of the data we collected
   ($\sim$2$\mu$s post-equilibration) is not always sufficient for extracting reliable
@@
   500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
-  sFLMcut). However, in the case of acetic acid, this may only happen because the 
-  Hurst parameter is overestimated. It appears we are operating on the border of the
-  minimum amount of data required to accurately parameterize the AD model. Longer
-  simulations and more independent trajectories may be necessary. Therefore, in 
-  the next section we will work with parameters fit to the full equilibrated portion
-  of the solute trajectories, doubling the data.
+  sFLMcut), but still appear to systematically under-predict the mean. We may be
+  operating on the border of the minimum amount of data required to accurately 
+  parameterize the AD model. Longer simulations and more independent trajectories may
+  be necessary. Therefore, in the next section we will work with parameters fit to the
+  full equilibrated portion of the solute trajectories, doubling the data.
+
+%  However, in the case of acetic acid, this may only happen because the 
+%  Hurst parameter is overestimated. It appears we are operating on the border of the
+%  minimum amount of data required to accurately parameterize the AD model. Longer
+%  simulations and more independent trajectories may be necessary. Therefore, in 
+%  the next section we will work with parameters fit to the full equilibrated portion
+%  of the solute trajectories, doubling the data.
 
@@
   order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
-  parameters extracted from MD simulations. The sFLMcut model and MSDDM yield 
+  parameters extracted from MD simulations. The sFLMcut AD model and MSDDM yield 
   similar predictions at a much greater computational cost due to the slow

### 2019-12-13 Ben_Manuscripts/stochastic_transport/figures/msd_comparison.py

@@ -86,8 +86,8 @@ sys = file_rw.load_object('%s/forecast_%s_%dstate.pl' % (directory, res, nmodes)
 dwell_dist = ['Power Law', 'Power Law Exponential Cutoff', 'Power Law', 'Power Law Exponential Cutoff']
 hop_dist = ['Gaussian', 'Gaussian', 'Levy', 'Levy']
 
-dwell_dist = ['Power Law Exponential Cutoff']
-hop_dist = ['Levy']
+#dwell_dist = ['Power Law Exponential Cutoff']
+#hop_dist = ['Levy']
 #dwell_dist = ['Power Law']
 #hop_dist = ['Levy']
 
@@ -148,7 +148,7 @@ for i, dists in enumerate(zip(dwell_dist, hop_dist)):
 			sys.determine_transition_matrix()
 			print(sys.count_matrix)
 		random_walks = CTRW(nsteps, ntraj, nmodes=nmodes, dt=dt, hop_dist=motion, dwell_dist=dwell, transition_count_matrix=sys.count_matrix if sys.nmodes > 1 else None)
-		random_walks.generate_trajectories(fixed_time=True, distributions=(sys.dwell_parameters, sys.hop_parameters, sys.hurst_distribution), discrete=True, ll=sys.dwell_lower_limit, max_hop=2*sys.max_hop, m=256, Mlowerbound=6000, nt=nt)
+		random_walks.generate_trajectories(fixed_time=True, distributions=(sys.dwell_parameters, sys.hop_parameters, sys.hurst_distribution), discrete=True, ll=sys.dwell_lower_limit, max_hop=2*sys.max_hop, m=256, Mlowerbound=256, nt=nt)
 
 		random_walks.calculate_msd(ensemble=False)
 		random_walks.bootstrap_msd(fit_linear=False)
@@ -164,6 +164,6 @@ for i, dists in enumerate(zip(dwell_dist, hop_dist)):
 plt.legend(labels, loc=0, fontsize=14)
 plt.tight_layout()
 #plt.savefig('toc_msd.png')
-plt.savefig('%dmode_msd_comparison_%s.pdf' % (nmodes,res))
+#plt.savefig('%dmode_msd_comparison_%s.pdf' % (nmodes,res))
 if not args.noshow:
 	plt.show()

### 2019-12-17 Ben_Manuscripts/stochastic_transport/Draft.tex
Speed improvements using a static empirical distribution

@@
   and methanol show considerable differences in their MSDs. Urea and acetic acid
-  appear to demonstrate satisfactory stationarity on the 5 $\mu$s timescale. The
-  shapes of their MSDs curves are also very similar (see Figure~\ref{S-fig:msd_comparison}
-  of the Supporting Information).
+  appear to demonstrate satisfactory stationarity. The shapes of their MSDs curves
+  are also very similar (see Figure~\ref{S-fig:msd_comparison} of the Supporting
+  Information).
 
@@
 
-  %BJC4: need figures to support these claims.
-  The non-stationary behavior of ethylene glycol and methanol present themselves
-  in different ways. On average, methanol molecules in the tails appear to be 
-  drifting further away from the pore center with time. Methanol's small size 
-  significantly increases the volume of accessible structural space. Ethylene 
-  glycol appears to experience an increased incidence of long trapping times. 
-  These problems probably cannot be addressed without more simulation time or 
-  additional solute trajectories.
+%  The non-stationary behavior of ethylene glycol and methanol present themselves
+%  in different ways. On average, methanol molecules in the tails appear to be 
+%  drifting further away from the pore center with time. Methanol's small size 
+%  significantly increases the volume of accessible structural space. Ethylene 
+%  glycol appears to experience an increased incidence of long trapping times. 
+%  These problems probably cannot be addressed without more simulation time or 
+%  additional solute trajectories.
 
@@
   solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
-  Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
-  intervals of the MD MSD curves, they appear to lie systematically below the mean. 
-  It is not clear whether this is a consistent feature of the AD model since we 
-  only used 2 solutes for this analysis.
+  %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
+  %intervals of the MD MSD curves, they appear to lie systematically below the mean. 
+  %It is not clear whether this is a consistent feature of the AD model since we 
+  %only used 2 solutes for this analysis.
 
@@
   From a qualitative perspective, the models only have moderate success at predicting
-  the shape of the MSD curves. Error in the MSD curvature can help explain some of
+  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
   the error in the predicted MSD magnitudes. The curves predicted for Urea with both 1 
@@
   This analysis also suggests that working with only half of the data we collected
-  ($\sim$2$\mu$s post-equilibration) is not always sufficient for extracting reliable
+  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
   parameter estimates. In most cases, the magnitude of the MSD predictions after a 
@@
 
-  We obtain reasonable predictions of the MD simulated MSDs when we parameterize the
-  AD model with all available data after the perceived equilibration time. We visualized the
+  We obtain reasonable predictions of the MD simulated MSDs when we parameterize the AD 
+  model with all available data after the perceived equilibration time. We visualized the
   parameters in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
@@
 
-  After a 1000 ns time lag, for all solutes except acetic acid, the 1 and 2 mode 
-  AD models do a fairly good job of predicting the magnitude of the MD 
-  MSD curves when we use truncated power laws. In all but one case (two mode 
-  ethylene glycol), MSD curves predicted by the sFLMcut model are higher than 
-  those predicted by the sFBMcut model because of the heavy tails of the L\'evy 
-  stable hop length distribution.
-
-  Qualitatively, the curves with the highest final MSDs (ethylene glycol and 
-  methanol) show more linear growth and their shapes are well captured by the
-  sFLMcut and sFBMcut AD models. The MSD curve of urea bends slightly and 
-  that of acetic acid has the most significant curvature. When the MD MSD 
-  curves bend, the MSD curves predicted by the sFBMcut model tends to more 
-  accurately portray their curvature since the sFLMcut model tends to become 
-  linear faster.
-
-  Acetic acid is a notable exception as no model accurately predicts its
-  MSD or curvature. Both sFBMcut and sFLMcut significantly over-predict the final
-  MSD while sFBM and sFLM significantly under-predict it. Once again, it 
-  appears that the Hurst parameter may be over-estimated. However, the parameters
-  of the hop and dwell distributions may be improved over those used to produce
-  Figures~\ref{fig:1mode_msd_comparison_ACH_train_front} and
-  \ref{fig:2mode_msd_comparison_ACH_train_front}. A lower value of $H$ would 
-  increase the curvature and reduce the AD predicted MSD to values more consistent
-  with acetic acid's MD MSD.
-
-  Despite their deviations from the MD, the ranking of the magnitude of predicted
-  MSDs remains the same as MD: ethylene glycol $\approx$ methanol $>$ urea $>$ acetic acid.
-%  The discrepancies between MD and the predictions of the AD model may be resolved
-%  by gathering longer and a greater quantity of solute trajectories
-  Therefore, we can use the current parameters to understand solute dynamics.
+  After a 1000 ns time lag, the 1 and 2 mode AD models do a fairly good job of 
+  predicting the magnitude of the MD MSD curves when we use truncated power
+  laws to describe the dwell time distributions. In most cases, the sFBMcut
+  and sFLMcut models give very similar results probably because their $\alpha_h$
+  parameter values are relatively close to 2, meaning the hop length distribution
+  is nearly Gaussian even when fit to a more general L\'evy distribution.
+
+  The deviation between the 1 mode MSD predictions and MD are primarily due
+  to differences in their curvature at long time lags. The shape and magnitude of the curves appears accurate 
+  at short time lags, however, the curves tend to undershoot the MD MSD mean
+  as the time lag increases. As discussed in the previous section, long time
+  positional anti-correlation may not exist in the MD system which results 
+  in a shift from sub-linear to linear MSD behavior. Acetic acid exemplifies
+  this point. At first glance, acetic acid's predicted MSD (sFLMcut and sFBMcut)
+  appear to match the curvature of MD quite well, but closer examination reveals
+  that the MD MSD curve actually shifts from a sub-linear to a linear regime 
+  around 500 ns.
+
+  The 2 mode models shows considerably less curvature at large time lags than
+  the 1 mode model because the implementation of the 2 mode model prevents long
+  timescale correlation. The width of the hop distribution changes every time
+  a switch between pores and tails occurs. We are unaware of an appropriate
+  technique which can correlate hops that come from different hop distributions, 
+  therefore every time a mode switch occurs, the correlation structure is 
+  broken. Solutes which switch between modes the least show the greatest
+  curvature. Methanol spends $> 90\%$ of its time in the tails, so mode transitions
+  are relatively rare and the predicted MSD has curvature. This artificially
+  solves the problem of long timescale correlation, however we do not recommend this
+  as it has no theoretical basis.
+
+  % In all but one case (two mode 
+  % ethylene glycol), MSD curves predicted by the sFLMcut model are higher than 
+  % those predicted by the sFBMcut model because of the heavy tails of the L\'evy 
+  % stable hop length distribution.
+
+%  Qualitatively, the curves with the highest final MSDs (ethylene glycol and 
+%  methanol) show more linear growth and their shapes are well captured by the
+%  sFLMcut and sFBMcut AD models. The MSD curve of urea bends slightly and 
+%  that of acetic acid has the most significant curvature. When the MD MSD 
+%  curves bend, the MSD curves predicted by the sFBMcut model tends to more 
+%  accurately portray their curvature since the sFLMcut model tends to become 
+%  linear faster.
+%  
+%  Acetic acid is a notable exception as no model accurately predicts its
+%  MSD or curvature. Both sFBMcut and sFLMcut significantly over-predict the final
+%  MSD while sFBM and sFLM significantly under-predict it. Once again, it 
+%  appears that the Hurst parameter may be over-estimated. However, the parameters
+%  of the hop and dwell distributions may be improved over those used to produce
+%  Figures~\ref{fig:1mode_msd_comparison_ACH_train_front} and
+%  \ref{fig:2mode_msd_comparison_ACH_train_front}. A lower value of $H$ would 
+%  increase the curvature and reduce the AD predicted MSD to values more consistent
+%  with acetic acid's MD MSD.
+
+%  Despite their deviations from the MD, the ranking of the magnitude of predicted
+%  MSDs remains the same as MD: ethylene glycol $\approx$ methanol $>$ urea $>$ acetic acid.
+%%  The discrepancies between MD and the predictions of the AD model may be resolved
+%%  by gathering longer and a greater quantity of solute trajectories
+%  Therefore, we can use the current parameters to understand solute dynamics.
 
@@
   $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
-  it appears that our model consistently under-predicts the methanol MSD curve relative
+  it appears that our model under-predicts the methanol MSD curve relative
   to other solutes. However, it remains plausible that methanol does have a low $H$ 
   value because it spends the majority of its time outside the pore region where collisions
-  with tails are frequent. Urea has the third highest MSD that is primarily a consequence of
-  more frequent and long dwell times, indicated by lower values of $\alpha_d$ and 
+  with tails are frequent. Urea has the third highest MSD which is primarily a consequence of
+  more frequent and longer dwell times, indicated by lower values of $\alpha_d$ and 
   $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
@@
   in the pore versus in the tails. It is clear that solutes are significantly slowed 
-  while they are in the tail region (mode 2) where long dwell times are more probable
+  while they are in the tail region where long dwell times are more probable
   (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
@@
   parameters can help us further understand solute dynamics. Hops appear to be well
-  modeled as anticorrelated draws from Gaussian and L\'evy stable distributions. 
+  modeled as anti-correlated draws from Gaussian and L\'evy stable distributions. 
   The data strongly suggests that one must truncate the power law dwell time 
@@
   in order to achieve good parameter estimates. The exact amount of data required 
-  is dependent on the solute studied. Solutes which achieve higher MSDs
-  in a given amount of time appear to be more accurately parameterized.
+  is dependent on the solute studied.
+
+  %Solutes which achieve higher MSDs
+  %in a given amount of time appear to be more accurately parameterized.
 
@@
   % BJC4: I moved this discussion up. It used to be after I presented the parameters
+  % BJC5: The pore/tail percentages could potentially go in the previous section, with
+  % the two-mode model.
   Solute size and chemical functionality influence which states are visited most frequently.
@@
   we believe this is unavoidable without at least an order of magnitude of additional data.
+  In theory, one could parameterize separate transition distributions for those
+  which occur in the tails versus in the pores, however this would lead to the same
+  issues shown by the anomalous diffusion model.
 
@@
   any trapping mechanism is likely caused by collisions with monomer head groups 
-  within the pore region. The Hurst parameters for transitional (T) emissions are 2-18 times higher 
-  than emissions from trapped states. The value of $\alpha_h$ for transition 
-  emissions is also relatively low giving higher probabilities to larger hops.
+  within the pore region. The Hurst parameters for transitional (T) emissions are up to 
+  18 times higher than emissions from trapped states. The value of $\alpha_h$ for 
+  transition emissions is also relatively low giving higher probabilities to larger hops.
 
@@
   width of the hop length distribution, $\sigma$, decreases while its L\'evy index,
-  $\alpha_h$, increases. Treating the tail and pore regions independently, $\sigma$
-  is largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding or 
-  associating with sodium (states 1 and 5). Solutes are free to move and take 
+  $\alpha_h$, increases. Treating states in the tail and pore regions independently, 
+  $\sigma$ is largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding
+  or associating with sodium (states 1 and 5). Solutes are free to move and take 
   occasionally large hops. The smallest $\sigma$ and highest $\alpha_h$ values are
@@
 
-  Using the parameters shown in Figure~\ref{fig:msddm_parameters}, we simulated 
-  1000 MSDDM trajectory realizations as described in Section~\ref{method:MSMs}
-  then calculated their MSDs. The MSDDM over-estimates solute MSDs by c.a. 250--650 \%
-  (see Figure~\ref{fig:msddm_performance}).
+  In most cases, The MSDDM predicts the magnitude of the MD MSDs within their 
+  1-$\sigma$ confidence intervals. Using the parameters shown in 
+  Figure~\ref{fig:msddm_parameters}, we simulated 1000 MSDDM trajectory 
+  realizations for each solute, as described in Section~\ref{method:MSMs},
+  then calculated their MSDs (see Figure~\ref{fig:msddm_performance}). Methanol's
+  MSD is over-predicted at short timescales while acetic acid's entire MSD 
+  curve is severely over-predicted.
 
@@
   \end{subfigure}
-  \caption{The MSD curves predicted by the MSDDM significantly over-predict the
-  magnitude and misrepresent the curvature of those generated from MD simulations.
-  We expect urea and acetic acid to show some curvature on these time scales.}\label{fig:msddm_performance}
+  \caption{In most cases, the magnitude of the MSD curves predicted by the 
+  MSDDM agree well with those generated from MD simulations. The predicted MSD
+  curves of urea and ethylene glycol lie within the 1-$\sigma$ confidence 
+  intervals of MD for all time lags. Methanol under-predicts the MSD at small
+  time lags and acetic acid grossly over-predicts the MSD at all time lags.
+  Like the anomalous diffusion model, the MSDDM doesn't fully capture the 
+  curvature of the MD MSD curves. }\label{fig:msddm_performance}
   \end{figure}
 
-  %It is clear that the predictive
-  %abilities of the MSDDM are inadequate but it is still possible to salvage
-  %key insights.
-
-  The MSDDM overestimates solute MSDs because correlation is lost every time a
-  state switch occurs. Although correlation exists within each sequence, there
-  is no memory of the previous state or state transition that can be built into
-  the first emission of the most recent state. This implies that the first 
-  value in a state sequence is a random draw from the underlying emission 
-  distribution. Frequent transitions between states lead to an abundance of 
-  short dwell times. It is difficult to accurately correlate short sequences so
-  we are almost simulating uncorrelated draws from the emission distribution.
-  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying the
-  transition matrix and simulating a simple 2-state model with parameters similar
-  to those in Table~\ref{table:msddm_params} (we tabulated the parameters used 
-  in Table~\ref{S-table:msddm_params} of the Supporting Information). We modified
-  the probability transition matrix, $T$, in order to control the probability of 
-  self-transitions (the diagonal elements of $T$). Larger self-transition 
-  probabilities lead to longer dwell times in each state. We set the off-diagonal
-  elements of $T$ to be equal values that make the rows of $T$ sum to unity when
-  combined with the self-transition probabilities. As we increase the 
-  self-transition probability, $T_{ii}$, the simulated MSD decreases. Consequently,
-  longer dwell times in each state allow us to more accurately simulate the
-  negative correlation that we observe in MD.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{T_sensitivity.pdf}
-  \caption{As we increase the self-transition probabilities ($T_{ii}$) of an MSDDM,
-  the simulated MSD of the process decreases because the negative correlation structure
-  of individual state sequences is simulated more accurately.}\label{fig:T_sensitivity}
-  \end{figure}
-
-  % MRS4: be more clear here what mechanistic insight it offers.
-  % BJC4: added a couple sentences after thesis
-  The MSDDM offers mechanistic insight but cannot be used for reliable predictions
-  of solute MSDs. We can obtain a detailed picture of dynamics within each state in
-  terms of the magnitude of their fluctuations and correlation with previous 
-  motion. Unfortunately correlation between adjacent same-state sequences is lost
-  with our model which causes the MSDs to be significantly over-predicted. The MSDDM
-  may be suitable for processes with rarer transitions between states. If we can 
-  further reduce the state-space of our models, it may have better predictive success,
-  but we lose mechanistic detail.
+  The dynamics of urea, ethylene glycol and, to a lesser extent, methanol 
+  appear to be well-captured by the MSDDM. One could argue that the curves
+  of ethylene glycol and urea are statistically indistinguishable. However, 
+  it's possible that they may diverge on longer timescales due to differences
+  in their curvature. Similarly, methanol's MD MSD is nearly linear while 
+  the MSDDM prediction is curving downward implying that it may underestimate
+  the MSD on longer timescales.
+
+  The predicted MSD of acetic acid is severely over-estimated most likely due
+  to poor parameterization. Acetic acid has a transitional Hurst parameter 
+  $\sigma$ values that are very similar to Urea. Consequently, the final 
+  magnitude of acetic acid's MSD actually lies just within the lower bound
+  of Urea's MD MSD 1-$\sigma$ confidence interval.
+
+  The MSDDM suffers similar shortcomings to the AD model. First, curvature 
+  on long timescales due to positional anti-correlation may result in 
+  underestimates of the MSD at large time lags. As suggested earlier, truncating
+  the positional autocorrelation function may help solve this issue. Second, 
+  parameterization can be challenging.
+
+  The MSDDM offers mechanistic insight and, in 3 out of 4 cases, gives reasonable
+  predictions of solute MSDs. We can used the MSDDM to obtain a detailed picture of dynamics within
+  each state in terms of the magnitude of their fluctuations and correlation with previous 
+  motion.
+
+%  Unfortunately correlation between adjacent same-state sequences is lost
+%  with our model which causes the MSDs to be significantly over-predicted. The MSDDM
+%  may be suitable for processes with rarer transitions between states. If we can 
+%  further reduce the state-space of our models, it may have better predictive success,
+%  but we lose mechanistic detail.
+
+% BJC5: following not true
+%  The MSDDM overestimates solute MSDs because correlation is lost every time a
+%  state switch occurs. Although correlation exists within each sequence, there
+%  is no memory of the previous state or state transition that can be built into
+%  the first emission of the most recent state. This implies that the first 
+%  value in a state sequence is a random draw from the underlying emission 
+%  distribution. Frequent transitions between states lead to an abundance of 
+%  short dwell times. It is difficult to accurately correlate short sequences so
+%  we are almost simulating uncorrelated draws from the emission distribution.
+%  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying the
+%  transition matrix and simulating a simple 2-state model with parameters similar
+%  to those in Table~\ref{table:msddm_params} (we tabulated the parameters used 
+%  in Table~\ref{S-table:msddm_params} of the Supporting Information). We modified
+%  the probability transition matrix, $T$, in order to control the probability of 
+%  self-transitions (the diagonal elements of $T$). Larger self-transition 
+%  probabilities lead to longer dwell times in each state. We set the off-diagonal
+%  elements of $T$ to be equal values that make the rows of $T$ sum to unity when
+%  combined with the self-transition probabilities. As we increase the 
+%  self-transition probability, $T_{ii}$, the simulated MSD decreases. Consequently,
+%  longer dwell times in each state allow us to more accurately simulate the
+%  negative correlation that we observe in MD.
+%  
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{T_sensitivity.pdf}
+%  \caption{As we increase the self-transition probabilities ($T_{ii}$) of an MSDDM,
+%  the simulated MSD of the process decreases because the negative correlation structure
+%  of individual state sequences is simulated more accurately.}\label{fig:T_sensitivity}
+%  \end{figure}
 

### 2019-12-20 Ben_Manuscripts/stochastic_transport/Draft.tex
Added missing figures

@@
   the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
-  The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
-  summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
+  %The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
+  %summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
 
@@
   Using the approach described above, we validated our 1 and 2 mode models with
-  urea and acetic acid, since their trajectories appear stationary. The 
-  resultant MSD plots are shown in Figure~\ref{fig:train_test}. We consider 
-  our models to match well if their predictions lie within the 1-$\sigma$
-  confidence intervals of the MD MSDs. We also look for qualitative agreement
-  in the shape of the curves.
+  urea and acetic acid, since their trajectories appear stationary. In 
+  Figure~\ref{fig:ad_eyetest}, we show that realizations of the AD model appear
+  qualitatively similar to those seen in our MD simulations (Figure~\ref{fig:solute_trajectories}).
+  The MSDs resulting from 1000 realizations of the AD model are shown in 
+  Figure~\ref{fig:train_test}. We consider the model's prediction to match well if the
+  MSD lies within the 1-$\sigma$ confidence intervals of the MD MSDs. We also
+  look for qualitative agreement in the shape of the curves.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{ad_realizations_1mode.pdf}
+  \caption{Simulations of 1 mode AD model trajectories for Urea display 
+  qualitatively similar hopping and trapping behavior to that shown in 
+  Figure~\ref{fig:solute_trajectories}. Analogous plots are shown for other solutes
+  %BJC5: todo: add plots to SI. Show I add a 2 mode model plot?
+  and the 2 mode mdoel in the Supporting Information. Dwell times may be exaggerated in the
+  sFBM and sFLM models because the power law dwell time distributions have infinite
+  variance.}\label{fig:ad_eyetest}
+  \end{figure}
 
@@
 
-  This brief analysis suggests two shortcomings of the AD model. First, positional
-  anti-correlation may diminish after a sufficiently long time lag, dependent on the 
+  This brief qualitative analysis suggests two shortcomings of the AD model. First, 
+  positional anti-correlation may dissipate after a sufficiently long time lag, dependent on the 
   solute being studied. Second, it is difficult to reliably parameterize the Hurst
@@
   \end{subfigure}
-  \caption{MSDs generated from realizations of our 1 mode anomalous diffusion models
-  agree well with MD-generated data when using an exponential cutoff (sFBMcut and SFLMcut).
-  When we do not apply an exponential cut-off to the dwell time distribution (sFBM 
-  and SFLM), MSDs are underpredicted. Drawing hops from a truncated L\'evy stable 
-  distribution results in higher MSDs than draws from Gaussians (sFLM and sFLMcut).}\label{fig:anomalous_msds_1mode}
+  \caption{In most cases, MSDs generated from realizations of our 1 mode anomalous
+  diffusion models agree well with MD-generated data when using an exponential cutoff
+  on the dwell time distribution (sFBMcut and SFLMcut). When we do not apply an 
+  exponential cut-off (sFBM and SFLM), MSDs are underpredicted. Drawing hops from a
+  truncated L\'evy stable distribution yields MSDs similar to when hops are drawn 
+  from Gaussian disributions (sFLM and sFLMcut).}\label{fig:anomalous_msds_1mode}
   \end{figure}
@@
   \end{subfigure}
-  \caption{MSDs generated from realization of our 2-mode anomalous diffusion model
-  also match well to MD-generated data. The MSD of urea appears to be underpredicted
-  by all model combinations. The MSD of ethylene glycol is predicted well when 
-  we draw dwell times from a power law distribution with an exponential cut-off.}\label{fig:anomalous_msds_2mode}
+  \caption{MSDs generated from realizations of our 2-mode anomalous diffusion model
+  predict the magnitude of the MSDs to a similar degree of accuracy as the 1 mode
+  model. Relative to the predictions of the 1 mode model the MSDs lack curvature because
+  the hop correlation structure is broken every time a transition between tails occurs.}\label{fig:anomalous_msds_2mode}
   \end{figure}
@@
   curvature. Methanol spends $> 90\%$ of its time in the tails, so mode transitions
-  are relatively rare and the predicted MSD has curvature. This artificially
+  are relatively rare and the predicted MSD has significant curvature. This artificially
   solves the problem of long timescale correlation, however we do not recommend this
@@
   while they are in the tail region where long dwell times are more probable
-  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
-  $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
+  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Each solute spends 
+  a different amount of time in the tails (see Figure~\ref{fig:AD_mode_occupation}). 
+  Urea and acetic acid spend slightly more than half of their time in the tails 
+  (56\% and 62\% of their time respectively) while ethylene glycol spends about 
+  44\% of its time in the tails. Urea and acetic acid's compact and flat structure 
+  allows it to more easily partition into the tails while ethylene glycol prefers
+  the pore region due to its two hydrophilic hydroxyl groups. Meanwhile methanol 
+  spends 91 \% of its time in the tails likely due to its small size.  
+  The value of $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
   is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
@@
   to make larger jumps to escape traps.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{AD_mode_occupation.pdf}
+  \caption{Solutes spend various amounts of time in the tail and pore region dependent
+  on their size, shape and chemical functionality. Methanol's small size favors 
+  occupation of the much larger accessible volume in the tails. Urea and acetic acid
+  are fairly stable in both regions since they are small and hydrophilic. Ethylene 
+  glycol is has a slight preference for the pores likely because it is a larger
+  molecule with two hydrophilic hydroxyl groups.}\label{fig:AD_mode_occupation}
+  \end{figure}
 
@@
   % BJC4: I moved this discussion up. It used to be after I presented the parameters
-  % BJC5: The pore/tail percentages could potentially go in the previous section, with
-  % the two-mode model.
   Solute size and chemical functionality influence which states are visited most frequently.
   In Figure~\ref{fig:state_probabilities}, we plotted the probabilities of occupying
-  a given state at any time. Urea and acetic acid spend slightly more than half 
-  their time in the tails (56\% and 62\% of their time respectively) while ethylene
-  glycol spends about 44\% of its time in the tails. Urea and acetic acid's compact
-  and flat structure allows it to more easily partition into the tails while ethylene
-  glycol prefers the pore region due to its two hydrophilic hydroxyl groups. Meanwhile
-  methanol spends 91 \% of its time in the tails likely due to its small size.
+  a given state at any time. Solutes tend to favor the same types of interactions 
+  independent of which region they are in.
+
+  % BJC5: moved to previous section  
+%   Urea and acetic acid spend slightly more than half of
+%  their time in the tails (56\% and 62\% of their time respectively) while ethylene
+%  glycol spends about 44\% of its time in the tails. Urea and acetic acid's compact
+%  and flat structure allows it to more easily partition into the tails while ethylene
+%  glycol prefers the pore region due to its two hydrophilic hydroxyl groups. Meanwhile
+%  methanol spends 91 \% of its time in the tails likely due to its small size.
 
@@
   \caption{Solutes spend varying amounts of time under the influence of each
-  trapping mechanism. Methanol spends the majority of its time in the tail region
-  while the rest of solute spend similar amounts of time in each region.}\label{fig:state_probabilities}
+  trapping mechanism. To aid the reader, we labeled each state with an abbreviation which
+  identifies the combination of conditions to which each solute is subject in each state:
+  t - tails, p - pores, h - hydrogen bonded, a - associated with sodium. Solutes tend to 
+  favor the same types of interactions (e.g. hydrogen bonding and/or associating with sodium
+  ions) independent of whether they are in the pores or the tails.}\label{fig:state_probabilities}
   \end{figure}
@@
   It does so 31\% of the total time while in the tails (state 3) and 21\% of the
-  total time while in the pores (state 7). The electron-dense and unshielded oxygen
-  atom of urea's carbonyl group is prone to associate with positively charged sodium
-  ions. The nitrogen atoms of urea are only weak hydrogen bond donors.
+  total time while in the pores (state 7). Note that sodium does not drift significantly 
+  into the tails but sits close to the pore/tail region boundary. The electron-dense 
+  and unshielded oxygen atom of urea's carbonyl group is prone to associate with 
+  positively charged sodium ions. The nitrogen atoms of urea are only weak hydrogen bond
+  donors.
 
@@
   Methanol spends most of its time unbound in the tail region (state 1) and spends a 
-  significant portion of time hydrogen bonded to while in the tail regions.
+  significant portion of time hydrogen bonded while in the tail regions.
   Most of the tail region hydrogen bonds are donated from methanol to the ether
@@
   In theory, one could parameterize separate transition distributions for those
-  which occur in the tails versus in the pores, however this would lead to the same
-  issues shown by the anomalous diffusion model.
+  which occur in the tails versus in the pores, however this would lead a broken 
+  correlation structure similar to that seen in the 2 mode AD model.
 
@@
   \caption{The parameters of the MSDDM are strong functions of trapping mechanisms.
-  We observe different parameters bu with similar trends between the tail and pore
-  region. The states are defined in Table~\ref{table:states}. To aid the reader, we 
-  labeled each state with an abbreviation which identifies the combination of 
-  conditions to which each solute is subject: t - tails, p - pores, h - hydrogen bonded, 
-  a - associated with sodium. The legend in (a) applies to all subplots. (a) Motion is
+  We observe different parameters but with similar trends between the tail and pore
+  region. The states are defined in Table~\ref{table:states}. See Figure~\ref{fig:state_probabilities}
+  for a description of the abbreviation under each state number. The legend in (a) applies to all subplots. (a) Motion is
   highly anti-correlated in trapped states. As the number of simultaneously influencing
@@
 
-  As solutes are influenced by more trapping interactions simultaneously (i.e. hydrogen
-  bonding \textit{and} associated with sodium versus just hydrogen bonding), the 
+  As solutes are influenced by more trapping interactions simultaneously (e.g.~hydrogen
+  bonding \textit{and} association with sodium versus just hydrogen bonding), the 
   width of the hop length distribution, $\sigma$, decreases while its L\'evy index,
@@
 
-  In most cases, The MSDDM predicts the magnitude of the MD MSDs within their 
-  1-$\sigma$ confidence intervals. Using the parameters shown in 
-  Figure~\ref{fig:msddm_parameters}, we simulated 1000 MSDDM trajectory 
-  realizations for each solute, as described in Section~\ref{method:MSMs},
-  then calculated their MSDs (see Figure~\ref{fig:msddm_performance}). Methanol's
-  MSD is over-predicted at short timescales while acetic acid's entire MSD 
-  curve is severely over-predicted.
+  Qualitatively, realizations of the MSDDM are not consistent with MD solute
+  trajectories. Using the parameters shown in Figure~\ref{fig:msddm_parameters}
+  we generated realizations of the MSDDM and plotted a typical realization for each
+  solute in Figure~\ref{fig:msddm_eyetest}. Except in rare cases, the solutes do not make
+  large hops. There are two reasons for this behavior. First, the width of 
+  hop length distributions are much smaller than those of the AD model. Closer
+  examination of Figure~\ref{fig:solute_trajectories} reveals that hops tend
+  to be an accumulation of a series of hops in the same direction. All of the 
+  hops in the MSDDM are negatively correlated which prevents this from happening.
+  The second reason is a consequence of using a single hop length distribution 
+  for transitions. Many transitions occur between two trapped states where the 
+  transitional hops are actually very small. Our model ignores this physical 
+  restriction which can cause the solute to drift rather than stay trapped.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{msddm_realizations.pdf}
+  \caption{Realizations of the MSDDM for each solute do not reproduce the hopping
+  and trapping behavior observed in our MD simulations. Except for a few large 
+  hops, the trajectories are qualitatively similar to what one might expect for
+  Brownian motion. Note that the length of the realizations are equal to the length
+  of the equlibrated portion of the MD trajectories for each solute.}\label{fig:msddm_eyetest}
+  \end{figure}
+
+  %Methanol's
+  %MSD is over-predicted at short timescales while acetic acid's entire MSD 
+  %curve is severely over-predicted.
 
@@
   curves of urea and ethylene glycol lie within the 1-$\sigma$ confidence 
-  intervals of MD for all time lags. Methanol under-predicts the MSD at small
+  intervals of MD for all time lags. Methanol over-predicts the MSD at small
   time lags and acetic acid grossly over-predicts the MSD at all time lags.
@@
 
-  The dynamics of urea, ethylene glycol and, to a lesser extent, methanol 
-  appear to be well-captured by the MSDDM. One could argue that the curves
+  Despite qualitative differences in trajectory realizations, the dynamics of 
+  urea, ethylene glycol and, to a lesser extent, methanol appear to be well-captured
+  by the MSDDM. We simulated 1000 MSDDM trajectory realizations for each solute, as
+  described in Section~\ref{method:MSMs}, then calculated their MSDs (see 
+  Figure~\ref{fig:msddm_performance}). In most cases, the MSDDM predicts the magnitude of the MD MSDs 
+  within their 1-$\sigma$ confidence intervals. One could argue that the curves
   of ethylene glycol and urea are statistically indistinguishable. However, 
@@
   The predicted MSD of acetic acid is severely over-estimated most likely due
-  to poor parameterization. Acetic acid has a transitional Hurst parameter 
-  $\sigma$ values that are very similar to Urea. Consequently, the final 
-  magnitude of acetic acid's MSD actually lies just within the lower bound
-  of Urea's MD MSD 1-$\sigma$ confidence interval.
+  to poor parameterization. As stated earlier, most of a solute's motion is 
+  due to displacements during state transitions. Acetic acid has a transitional
+  Hurst parameter close to Urea's and a transitional $\sigma$ value that 
+  is higher than urea's. This suggests that the heavier tails of urea's transitional
+  hop distribution (greater $\alpha_h$ value) are in large part responsible for 
+  urea's higher predicted MSD. Although we note that acetic acid's predicted MSD
+  actually lies just within the lower bound of Urea's MD MSD 1-$\sigma$ 
+  confidence interval. There is also the strong possibility that the over-estimate is
+  a consequence of lumping together all of acetic acid's transitional hops into
+  a single correlated distribution.
 
@@
   the positional autocorrelation function may help solve this issue. Second, 
-  parameterization can be challenging.
+  parameterization can be challenging. In addition to possibly poor estimates 
+  of the Hurst parameter, we made the simplifying assumption that we could lump
+  all transitional hops into a single distribution. While this appears to work
+  in most cases, it is the source of qualitative mismatches between MSDDM
+  realations and MD simulation trajectories and it may be the source of the 
+  over-estimate of acetic acid's MSD.
 
   The MSDDM offers mechanistic insight and, in 3 out of 4 cases, gives reasonable
-  predictions of solute MSDs. We can used the MSDDM to obtain a detailed picture of dynamics within
-  each state in terms of the magnitude of their fluctuations and correlation with previous 
-  motion.
+  predictions of solute MSDs. To successfully apply the model, one must know 
+  representative discrete states beforehand or apply some technique to identify
+  them. At the very least, we can used the MSDDM to obtain a detailed quantitative
+  picture of dynamics within each state in terms of the magnitude of their 
+  fluctuations and correlation with previous motion. If we have confidence in
+  their predictive ability, then we can project solute trajectories out to 
+  macroscopic timescales and estimate macroscopic observables such as solute 
+  flux and selectivity.
 
@@
   We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
-  diffusion model in order to demonstrate how one can use its realizations in
-  order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
-  parameters extracted from MD simulations. The sFLMcut AD model and MSDDM yield 
-  similar predictions at a much greater computational cost due to the slow
-  generation of fractional L\'evy noise.
+  diffusion model and the MSDDM in order to demonstrate how one can use their realizations
+  in order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
+  parameters extracted from MD simulations. The 1-mode sFBMcut mode generates predictions
+  similar to the 1-mode sFLMcut model at a lower computational cost and is far more
+  accurate than sFBM and sFLM. The 2-mode model has a broken correlation structure, so 
+  we do not consider it here.
+
   %MRS5: One question is if other method would lead to substantially
@@
   %about justification more if just one method is mentioned.
-  %BJC5: would love to test MSDDM against this but I don't know how to make 
-  % the algorithm faster. It already uses an FFT to correlate the data (to which I pass powers of 2)
+  %BJC5: Added MSDDM
 
@@
   24 cores to simulate trajectory realizations in parallel, it takes on the order 
-  of 1 day to simulate 10000 realizations of solutes traversing a 50 nm pore. The 
-  RAM requirements and performance scales greater than linearly and thus would 
-  take an infeasible amount of memory and time to simulate transport through a 
-  pore over 100 times longer.
+  of 1 day to simulate 10000 sFBMcut realizations of solutes traversing a 50 nm pore.
+  The computational requirements of the MSDDM are about 10 times longer. For both
+  models, the RAM requirements and performance scales greater than linearly and 
+  thus would take an infeasible amount of memory and time to simulate transport 
+  through a pore over 100 times longer.
 
@@
   %BJC5: added this
-  Although we used 10000 trajectory realizations in order to generate 
-  Figure~\ref{fig:flux_curves}, one may actually need considerably less realizations
-  in order to predict and compare flux between solutes. In Figure~\ref{S-fig:flux_curve_sensitivity}
+  It is only necessary to simulate 1000 realizations of each model in order to
+  parameterize Equation~\ref{eqn:flux_decay}. We used 10000 trajectory realizations 
+  in order to generate Figure~\ref{fig:flux_curves}, however, in Figure~\ref{S-fig:flux_curve_sensitivity}
   of the Supporting information, we show that one can still show statistically
   significant differences in solute flux with as little as 100 trajectory 
-  realizations.
+  realizations. To be sure, we recommend simulating at least 1000 realizations. 
+  Since the computational cost of the MSDDM is greater than the AD model, we 
+  generated flux curves using only 1000 realizations at each pore length.
 
@@
   We have tested two different mathematical frameworks for describing solute
-  motion in an H\textsubscript{II} phase LLC membrane. The values obtained for
-  the parameters when fitting the models to the time series data offer important
-  mechanistic insight on the molecular details of transport.
+  motion by applying them to an H\textsubscript{II} phase LLC membrane. The values
+  obtained for the parameters when fitting the models to the time series data 
+  offer important mechanistic insight on the molecular details of transport.
   Subordinated fractional Brownian and L\'evy motion have a nice theoretical 
@@
   quantifies and allows comparison of the hopping and trapping behavior 
-  between solutes. A two mode model that describes dynamics based on whether
+  among solutes. A two mode model that describes dynamics based on whether
   a solute is in or out of the pore region allows us to break down individual
@@
   solutes among states as well as the type of stochastic behavior shown in each 
-  state. However, it doesn't accurately portray correlated time series behavior
-  leading to overpredicted MSDs.
-
-  %MRS4: test/train in order to show power?
-  We believe that our models have moderate predictive power. 
-  %MRS4: be more precise on how superior is quantified below.
-  The anomalous
-  diffusion model has superior performance to the MSDDM. Both 1 and 2 mode 
-  sFBM and sFLM with truncated power law distributions predict MSDs close 
-  to those simulated with MD while the MSDDM significantly over-predicts MSDs.
-  One might have more success using the MSDDM with a system that exhibits
-  infrequent transitions between states.
+  state.
+
+  All of the models we tested have moderate success reproducing the MSDs of
+  solute trajectories generated by MD simulations. In almost all cases, large 
+  portions of the MSDs predicted by our model fall within the 1-$\sigma$
+  confidence intervals of MD. Aside from inaccuracies in parameter estimates,
+  the most significant shortcoming of all models is their ability to 
+  accurately portray the curvature of the MSD curves. The MD MSD curves tend
+  to  become linear on long timescales, but the MSD curves generated by our
+  models have persistent curvature that may cause them to under-predict
+  the MSD on very long timescales.
+
+  We demonstrated how one could used our models in order to to determine
+  macroscopic flux and selectivity.
+  %BJC5: I'll write the rest of this paragraph after I finish the MSDDM flux calculations.
 

### 2019-12-20 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
New figures + speed improvements
Added missing figures

@@
   similar MSDs, providing evidence of stationarity, while the MSDs of 
-  ethylene glycol and methanol are different.}\label{fig:msd_comparison}
+  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
   \end{figure}
@@
   \begin{figure}
+  \centering
   \includegraphics[width=0.5\textwidth]{flux_curves_brownian.pdf}
@@
   \caption{}\label{fig:mfpt_curve_brownian}
+  \end{figure}
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
+  \caption{100 Independent Trajectories}\label{fig:N100}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
+  \caption{1000 Independent Trajectories}\label{fig:N1000}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
+  \caption{5000 Independent Trajectories}\label{fig:N5000}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
+  \caption{10000 Independent Trajectories}\label{fig:N10000}
+  \end{subfigure}
+  \caption{Even using a small number of independent trajectories, one can
+  reliably calculate flux as a function of pore length. The uncertainty in
+  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
   \end{figure}

### 2019-12-31 Ben_Manuscripts/stochastic_transport/Draft.tex
New charts explaining beta parameter

@@
   diffusion model and the MSDDM in order to demonstrate how one can use their realizations
-  in order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
+  in order to calculate the flux (see section~\ref{method:mfpt}) of solutes given model 
   parameters extracted from MD simulations. The 1-mode sFBMcut mode generates predictions
   similar to the 1-mode sFLMcut model at a lower computational cost and is far more
-  accurate than sFBM and sFLM. The 2-mode model has a broken correlation structure, so 
-  we do not consider it here.
-
-  %MRS5: One question is if other method would lead to substantially
-  %different results for fluxes or selectivity.  May need too think
-  %about justification more if just one method is mentioned.
-  %BJC5: Added MSDDM
-
-  %MRS5: I think it might be useful to have at least visualizions of
-  %distribution of FPT and its fit. It might not be obvious to
-  %readers that the different mechanisms have distributions of FPT
-  %that are well decscribed by the relatively simple moving diffusion
-  %equation in eq 15. 
-  %BJC5: added to figure
+  accurate than sFBM and sFLM. The 2-mode AD model has a broken correlation structure, 
+  so we do not consider it here.
 
@@
   and used the expected value of the analytical equation to calculate flux from 
-  Equation~\ref{eqn:hill_relation}. As shown in Figure~\ref{fig:flux_curves}, 
-  the flux appears to scale according to a power law of the form:
+  Equation~\ref{eqn:hill_relation}. As shown in Figures~\ref{fig:flux_curves_ad} and
+  \ref{fig:flux_curves_msddm}, the flux appears to scale according to a power law 
+  of the form:
   \begin{equation}
@@
   \centering
-  \begin{subfigure}{0.475\textwidth}
+  %BJC5: TODO: make same figure for msddm
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{fpt_distributions.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.475\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{flux_curves.pdf}
-  \caption{}\label{fig:flux_curves_regular}
-  \end{subfigure}
+  \caption{sFBMcut}\label{fig:flux_curves_ad}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_msddm.pdf}
+  \caption{MSDDM}\label{fig:flux_curves_msddm}
+  \end{subfigure}  
+  \caption{(a) The distributions of passage times generated from the sFBMcut model
+  fit well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
+  solutes as well as the MSDDM in Figures~\ref{S-fig:ad_fpt_fits} and~\ref{S-fig:msddm_fpt_fits}
+  of the Supporting Information. (b) The single particle flux measured 
+  by the sFBMcut AD model and (c) the MSDDM decays with increasing pore length. 
+  The rankings of solute fluxes are consistent with the MSDs predicted by each model.
+  The ranking of the MSDDM is most consistent with MD MSDs. The MSDDM predicts higher
+  fluxes than the sFBMcut model. We fit the single particle solute flux versus pore
+  length, $L$, to a power law function of the form $cL^{-\beta}$ (dashed lines in (b)
+  and (c)). 
+%  Solutes with higher fluxes have higher values of $c$. Solutes with 
+%  smaller Hurst parameters, $H$, have larger values of $\beta$. (c) If we remove 
+%  correlation between hops (set $H$=0.5), the flux increases significantly and 
+%  $\beta \sim 2$ for all solutes independent of dwell distribution
+%  parameters.
+  }\label{fig:flux_curves}
+  \end{figure}
+
   % BJC: could use better color scheme. Maybe outline hurst parameters
-  \begin{subfigure}{0.475\textwidth}
-  \includegraphics[width=\textwidth]{c_parameters.pdf}
-  \caption{}\label{fig:c_parameters}
-  \end{subfigure}
-  \begin{subfigure}{0.475\textwidth}
-  \includegraphics[width=\textwidth]{beta_parameters.pdf}
-  \caption{}\label{fig:beta_parameters}
-  \end{subfigure}
+%  \begin{subfigure}{0.475\textwidth}
+%  \includegraphics[width=\textwidth]{c_parameters.pdf}
+%  \caption{}\label{fig:c_parameters}
+%  \end{subfigure}
+%  \begin{subfigure}{0.475\textwidth}
+%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
+%  \caption{}\label{fig:beta_parameters}
+%  \end{subfigure}
 %  \begin{subfigure}{0.475\textwidth}
@@
   % have each just show 1 point?
-  \caption{(a) The single particle solute flux decays with increasing pore length. 
-  Solutes with high MSDs have higher fluxes. (b) We fit the single particle solute flux 
-  versus pore length, $L$, to a power law function of the form $cL^{-\beta}$ (dashed 
-  lines in (a)). Solutes with higher fluxes have higher values of $c$. Solutes with 
-  smaller Hurst parameters, $H$, have larger values of $\beta$. (c) If we remove 
-  correlation between hops (set $H$=0.5), the flux increases significantly and 
-  $\beta \sim 2$ for all solutes independent of dwell distribution
-  parameters.}\label{fig:flux_curves}
+
+  We determined that it is only necessary to simulate 1000 realizations of each model
+  in order to parameterize Equation~\ref{eqn:flux_decay}. We used 10000 trajectory
+  realizations in order to generate each point in Figure~\ref{fig:flux_curves_ad}, 
+  however, in Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting information,
+  we show that one can still show statistically significant differences in solute 
+  flux, with minimal change to the mean flux values, using as few as 100 trajectory
+  realizations. To be sure, we recommend simulating at least 1000 realizations. 
+  Since the computational cost of the MSDDM is greater than the AD model, we generated
+  each point of the flux curves in Figure~\ref{fig:flux_curves_msddm} using only 1000
+  realizations at each pore length.
+
+  Anti-correlation between solute hops has a significant effect on the scaling
+  of solute flux with pore length. In Figure~\ref{fig:beta_hurst}, we show that 
+  $\beta$, as derived from the sFBMcut model, is inversely related to the Hurst
+  parameter while $\beta$, as derived from the MSDDM, shows no discernible
+  trend.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.43\textwidth}
+  \includegraphics[width=\textwidth]{beta_hurst.pdf}
+  \caption{}\label{fig:beta_hurst}
+  \end{subfigure}
+  \begin{subfigure}{0.52\textwidth}
+  \includegraphics[width=\textwidth]{beta_parameters.pdf}
+  \caption{}\label{fig:beta_parameters}
+  \end{subfigure}
   \end{figure}
 
-  %MRS5: Does't fitting to eq 15 cut down on the expense of the number of trajectories
-  %by a fair amount?  Should there be some discussion of this? 
-  %BJC5: added this
-  It is only necessary to simulate 1000 realizations of each model in order to
-  parameterize Equation~\ref{eqn:flux_decay}. We used 10000 trajectory realizations 
-  in order to generate Figure~\ref{fig:flux_curves}, however, in Figure~\ref{S-fig:flux_curve_sensitivity}
-  of the Supporting information, we show that one can still show statistically
-  significant differences in solute flux with as little as 100 trajectory 
-  realizations. To be sure, we recommend simulating at least 1000 realizations. 
-  Since the computational cost of the MSDDM is greater than the AD model, we 
-  generated flux curves using only 1000 realizations at each pore length.
-
-  %MRS: can you put a physical thesis here, not just a mathematical one?  Why is this change in parameters important to flux?
-  The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
-  solute MSD while the value of the growth exponent, $\beta$, is inversely 
-  related to the Hurst parameter, $H$ (see Figure~\ref{fig:flux_parameters}).
-  In Figure~\ref{fig:flux_curves_brownian}, we removed the correlation 
-  structure (set $H$=0.5) from AD trajectory realizations so that all hops 
-  were uncorrelated. Regardless of the parameters of the dwell time distribution,
-  the growth exponent is always about 2, the same value that we observe for 
-  Brownian motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the 
-  Supporting Information).
+%  \begin{figure}
+%  \centering
+%  % bar charts
+%%  \begin{subfigure}{0.45\textwidth}
+%%  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
+%%  \end{subfigure}
+%%  \begin{subfigure}{0.45\textwidth}
+%%  \includegraphics[width=\textwidth]{beta_parameter_comparison.pdf}
+%%  \end{subfigure}
+%  \includegraphics[width=0.5\textwidth]{beta_c_parameter_comparison.pdf}
+%  \caption{}\label{fig:flux_parameters}
+%  \end{figure}
 
@@
   %information, and you just state the result here.
-
-  Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
-  highlights that anti-correlation between hops plays a major role in solute flux.
-  With a pore length of 50 nm, the flux of the fasted moving solute, ethylene glycol is 
-  c.a. 5 times lower with versus without anti-correlated hops. The flux of the slowest
-  moving solute, acetic acid, is about 16 times lower by the same comparison. This 
-  difference will only grow with increasing pore length. Note also that the ranking
-  of solute fluxes changes. Methanol jumps from the second lowest to the highest
-  flux when we remove hop correlation. The high degree of anti-correlation among
-  hops made by methanol outweighs its relatively wide hop length distribution.
+  %MRS: can you put a physical thesis here, not just a mathematical one?  Why is this change in parameters important to flux? 
+%  The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
+%  solute MSD while the value of the growth exponent, $\beta$, is inversely 
+%  related to the Hurst parameter, $H$ (see Figure~\ref{fig:flux_parameters}).
+%  In Figure~\ref{fig:flux_curves_brownian}, we removed the correlation 
+%  structure (set $H$=0.5) from AD trajectory realizations so that all hops 
+%  were uncorrelated. Regardless of the parameters of the dwell time distribution,
+%  the growth exponent is always about 2, the same value that we observe for 
+%  Brownian motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the 
+%  Supporting Information).
+
+% BJC: following is wrong
+%  Dwell times between hops have a significant effect on the length dependence
+%  of solute flux. The values of $\beta$ fit to realizations of the sFBMcut AD
+%  model are significantly higher than the MSDDM. As evident by comparison of 
+%  Figures~\ref{fig:msddm_eyetest} and~\ref{fig:ad_eyetest}, realizations of the
+%  AD model exhibit much longer and more frequent periods of immobility. If we
+%  generate realizations of the sFBMcut model without trapping (dwell times are
+%  all 1 time step), the value of $\beta$ drops to 2 in all cases. In fact, we
+%  observe the same value of $\beta$ for Brownian motion (see Figure blah of the 
+%  Supporting Information) which implies that the Hurst parameter has no effect
+%  on the length dependence of flux.
+%  
+%  Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
+%  highlights that anti-correlation between hops plays a major role in solute flux.
+%  With a pore length of 50 nm, the flux of the fasted moving solute, ethylene glycol is 
+%  c.a. 5 times lower with versus without anti-correlated hops. The flux of the slowest
+%  moving solute, acetic acid, is about 16 times lower by the same comparison. This 
+%  difference will only grow with increasing pore length. Note also that the ranking
+%  of solute fluxes changes. Methanol jumps from the second lowest to the highest
+%  flux when we remove hop correlation. The high degree of anti-correlation among
+%  hops made by methanol outweighs its relatively wide hop length distribution.
 

### 2019-12-31 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
New charts explaining beta parameter

@@
 %  particle with 2 absorbing boundaries.
+  \subsection*{Analytical fits to MFPT distributions}
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{flux_curves_brownian.pdf}
-  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ad_fpt_distributions_URE.pdf}
+  \caption{Urea}\label{fig:URE_ad_fpt_distributions}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ad_fpt_distributions_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:ACH_ad_fpt_distributions}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ad_fpt_distributions_GCL.pdf}
+  \caption{Ethylene Glycol}\label{fig:GCL_ad_fpt_distributions}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ad_fpt_distributions_MET.pdf}
+  \caption{Methanol}\label{fig:MET_ad_fpt_distributions}
+  \end{subfigure}
+  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
+  first passage time distributions generated by 10,000 realizations of the 
+  anomalous diffusion model. }\label{fig:ad_fpt_fits}
   \end{figure}
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{mfpt_curves_brownian.pdf}
-  \caption{}\label{fig:mfpt_curve_brownian}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msddm_fpt_distributions_URE.pdf}
+  \caption{Urea}\label{fig:URE_msddm_fpt_distributions}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msddm_fpt_distributions_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:ACH_msddm_fpt_distributions}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msddm_fpt_distributions_GCL.pdf}
+  \caption{Ethylene Glycol}\label{fig:GCL_msddm_fpt_distributions}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msddm_fpt_distributions_MET.pdf}
+  \caption{Methanol}\label{fig:MET_msddm_fpt_distributions}
+  \end{subfigure}
+  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
+  first passage time distributions generated by 1000 realizations of the 
+  Markov state dependent dynamical model. Note that we generated 10 times less
+  realizations of the MSDDM which leads to noisier histograms. We show that
+  this has a negligible effect on the fits in Figure~\ref{fig:flux_curve_sensitivity}.}\label{fig:msddm_fpt_fits}
   \end{figure}
+
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{flux_curves_brownian.pdf}
+%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
+%  \end{figure}
+%  
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{mfpt_curves_brownian.pdf}
+%  \caption{}\label{fig:mfpt_curve_brownian}
+%  \end{figure}
+
   \begin{figure}

### 2020-01-01 Ben_Manuscripts/stochastic_transport/Draft.tex
Better explanations of beta

@@
 
-  Anti-correlation between solute hops has a significant effect on the scaling
-  of solute flux with pore length. In Figure~\ref{fig:beta_hurst}, we show that 
-  $\beta$, as derived from the sFBMcut model, is inversely related to the Hurst
-  parameter while $\beta$, as derived from the MSDDM, shows no discernible
-  trend.
+  %The scaling of solute flux with pore length is a complicated function of hop and 
+  %dwell parameters, however, anti-correlation between solute hops appears to
+  %be the most significant influencing factor. 
+  The scaling of solute flux with pore length is primarily influenced by anti-correlation
+  between solute hops. In Figure~\ref{fig:beta_hurst}, we show that $\beta$, as derived 
+  from the sFBMcut model, is inversely related to the Hurst parameter. This makes intuitive
+  sense since higher degrees of anti-correlation should slow the rate at which solutes
+  cross the membrane pore. $\beta$, as derived from the MSDDM, appears approximately 
+  constant but this is consistent with nearly invariant transitional Hurst parameters
+  (see Figure~\ref{fig:H_v_state}). However, Figure~\ref{fig:beta_hurst} does raise
+  the question as to why $\beta$ is so much lower than the sFBMcut model.
+
+  To understand the behavior of the MSDDM, we studied the $\beta$ parameter derived 
+  from variations on each model, visualized in Figure~\ref{fig:beta_parameters}. First, 
+  we removed anti-correlation between hops in the sFBMcut trajectory (set $H$=0.5). 
+  The $\beta$ parameter drops to values similar to the MSDDM. When we remove anti-correlation
+  \textit{and} dwell times between hops (set dwell times equal to 1), effectively simulating 
+  Brownian motion, we observe similar $\beta$ parameters. These two variations imply that,
+  in the AD models, the $\beta$ parameter is only a function of $H$ and not dependent on
+  dwell times ($\alpha_d$) or hop lengths ($\sigma$). The MSDDM is fundamentally similar to 
+  the AD model in that one makes correlated draws from a hop distribution. Therefore,
+  we should expect the $\beta$ value of the MSDDM to be larger than that of Brownian 
+  motion.
+  %Although the dwell times are
+  %insignificant compared to the AD model (compare Figures~\ref{fig:ad_eyetest} and
+  %\ref{fig:msddm_eyetest} for example), we have just shown
+
+  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
+  itself as well as inaccuracies resulting from of simulation of very long FLM trajectories.
+  Turning first to the model itself, we have designed it to ensure that the magnitude of the
+  hops in the series of transitions between states are anti-correlated from start to finish. 
+  This assumes that the transition correlation structure is unaffected by the
+  sub-trajectories between each state transition. Each time a state transition occurs, one
+  must initialize a new time series sub-trajectory with its own correlation structure. 
+  Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
+  in each state is relatively short making the accuracy of the correlation structure 
+  questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
+  $\sigma$ in trapped states. Since we add the transitional hop lengths to each end of
+  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
+  to one another largely decorrelating them. We tested this reasoning by modifying the 
+  MSDDM to completely immobilize particles except when they transition between states. 
+  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
+  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
+  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
+  In short, it is computationally infeasible to use enough terms to accurately incorporate
+  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
+  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
+  fractional Brownian motion, for which we have an exact simulation method, in place of 
+  FLM. When we use FBM, $\beta$ increases well above the Brownian value. $\beta$ increases
+  even further if we immobilize the trapped states. Thus the low value of $\beta$ of the
+  MSDDM is a consequence of model assumptions and inexact simulation of FLM.
 
@@
   \end{subfigure}
+  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
+  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
+  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
+  sub-trajectories between state transitions decorrelate transitional hops and because
+  our FLM simulation procedure does not accurately correlate hops after long time lags. 
+  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
+  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
+  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
+  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
+  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
+  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
+  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
+  \end{figure}
+
+  The values of $c$ are likely a complex function of $\sigma$, $alpha_d$, $H$ and $\alpha_d$
+  where applicable. The values of $c$ scale the flux curves and are directly correlated to 
+  flux magnitude. We showed earlier that $\beta$ is not a function of $\sigma$ or $\alpha_d$,
+  therefore dwell times and hop lengths must influence $c$. In fact, any parameter which acts
+  to modify the rate at which solutes move through the membrane pores will affect $c$.
+  Therefore it is sensible to hypothesize that a higher degree of anti-correlation (lower $H$)
+  should decrease $c$ and a higher value of $\alpha_h$ should also increase $c$.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
+  \caption{}\label{fig:c_parameters}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
+  \caption{}\label{fig:c_influence}
+  \end{subfigure}
+  \caption{(a) The c paramters are directly related to your mom (b) }\label{fig:c}
   \end{figure}
@@
 
-  % Partially in methods?
   The power law decay of the flux with pore length implies the following relationship
@@
   When $\beta$ values are equal, as is the case for uncorrelated motion, selectivity only
-  depends on the pre-factors, $c$. 
+  depends on the pre-factors, $c$. In most cases, the length dependence of selectivity 
+  plateaus quickly which implies that a coating of LLC membrane with a thickness on the 
+  order of those already made experimentally should be sufficiently optimal. 
   %MRS5?
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{selectivity.pdf}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{selectivity.pdf}
+  \caption{sFBMcut}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{selectivity_msddm.pdf}
+  \caption{MSDDM}
+  \end{subfigure}
   \caption{The selectivity of 2 species changes monotonically with pore length. The
-  strength of dependence on pore length depends on the difference between $\beta$ values.}
+  strength of dependence on pore length depends on the difference between $\beta$ values.
+  The selectivities predicted by the sFBMcut AD model (a) are much larger in magnitude than
+  those predicted by the MSDDM (b) because predictions of the AD model result in a much
+  larger variation in flux (compare Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm}).}
   \label{fig:selectivity}
   \end{figure}
+
+  The selectivities predicted by the sFBMcut model are both higher in magnitude and
+  ordered differently than the those predicted by the MSDDM. The magnitudes of the
+  sFBMcut predictions are higher because the predicted solute fluxes vary more widely
+  than those predicted by the MSDDM (compare Figures~\ref{fig:flux_curves_ad} 
+  and~\ref{fig:flux_curves_msddm}). The ordering is different mostly because the 
+  ordering of the flux predictions is different.
+
+  We cannot say with absolute certainty which selectivity curves are more 
+  trustworthy. The sFBMcut model uses exact simulation techniques and yields 
+  qualitatively accurate solute trajectories, but it may overestimate long 
+  timescale correlation present in the real system. For this reason, we might
+  expect the $\beta$ values of the true flux curves to be closer to the 
+  Brownian value as exhibited by the MSDDM. But the MSDDM yields qualitatively
+  inaccurate solute trajectories and we do not have a good understanding of
+  how to precisely control the point at which solute hops become decorrelated.
+
+  However, we may gain the most by using the two models in tandem. In both cases,  
+  the data suggests that this particular LLC membrane might be most useful for 
+  selectively separating ethylene glycol from acetic acid.
 
@@
   %MRS3: add specific info for PRF and GAANN
-  %BJC3: I don't know the PRF info. I wrote GAANN as I did on the last paper which is what Rob Davis told me to do
-  %MRS4: I willō track down the PRF grant number (if typical)
+  %BJC3: I wrote GAANN as I did on the last paper which is what Rob Davis told me to do
   This work was supported in part by the ACS Petroleum Research Fund grant \#59814-ND7
@@
   Colorado Boulder and Colorado State University.
+
+  We would also like to thank Richard Noble for helping us make the connection 
+  between the empirical mean first passage time distribution and the analytical
+  equation to which we fit the distributions (Equation~\ref{eqn:passage_times}).
 

### 2020-01-01 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Better explanations of beta

@@
 \documentclass{article}
+
+% Table of contents formatting
+\usepackage{tocloft}
+
+\renewcommand\cftsecfont{\normalfont}
+\renewcommand\cftsecpagefont{\normalfont}
+\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}}
+\renewcommand\cftsecdotsep{\cftdot}
+\renewcommand\cftsubsecdotsep{\cftdot}
+\cftsetindents{section}{0em}{3em}
+%\cftsetindents{subsection}{1em}{3em}
+
 \usepackage{graphicx}
@@
   \maketitle
+  \tableofcontents
   \graphicspath{{./supporting_figures/}}
   \bibliographystyle{ieeetr}
+
+  \newpage
 
@@
   \texttt{/analysis/ markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
+  \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD or MSDDM model. \\\hline
 
@@
 
+  \newpage
+
   \section{Solute Equilibration}\label{section:equilibration}
@@
 
-  \begin{figure}
+  \begin{figure}[hb]
   \centering
@@
   the fastest, after 1000 ns. (b) Ethylene glycol equilibrates after 1200 ns 
-  (c) Acetic Acid does not equilibrate until 4400 ns. (d) We considered methanol
-  to be equilibrated after 3500 ns. Methanol nearly completely partitions into
-  the tails.}\label{fig:equilibration}
+  (c) The partition of acetic acid appears oscillate slowly. We considered it to be
+  equilibrated after 2000 ns. (d) We considered methanol to be equilibrated after
+  3500 ns. Methanol nearly completely partitions into the tails.}\label{fig:equilibration}
   \end{figure}
@@
   \newpage
+
   \section{Estimating the Hurst Parameter}\label{section:H_estimate}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{hurst_autocorrelation.pdf}
-  \caption{The analytical autocorrelation function of FBM decays to zero faster when 
-  H $<$ 0.5 compared to when H $>$ 0.5.}\label{fig:hurst_autocorrelation}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{hurst_autocorrelation.pdf}
+  \caption{}\label{fig:hurst_autocorrelation}
+  \end{subfigure}
+  % supporting_figures/flm_autocov.py
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flm_autocovariance.pdf}
+  \caption{}\label{fig:flm_autocorrelation}
+  \end{subfigure}
+  \caption{(a) The analytical autocorrelation function of FBM decays to zero faster
+  when H $<$ 0.5 compared to when H $>$ 0.5. (b) The autocorrelation function of an 
+  FLM process does not change with increasing sequence length (N). It shares the same
+  autocorrelation function as fractional Brownian motion (FBM). All sequenced used to
+  make this plot were generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
   \end{figure}
@@
   function, does not change with increasing sequence length. Additionally, the
-  autocorrelation function of FBM, with the same $H$, is the same.
+  autocorrelation function of FBM, with the same $H$, is the same. Therefore we are 
+  confident that we can use the same Hurst parameter as an input to both FBM and FLM
+  simulations.
 
-  % supporting_figures/flm_autocov.py
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{flm_autocovariance.pdf}
-  \caption{The autocorrelation function of an FLM process does not change with 
-  increasing sequence length (N). It shares the same autocorrelation function as
-  fractional Brownian motion (FBM). All sequenced used to make this plot were 
-  generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:flm_autocorrelation}
-  \end{figure}
+  \newpage
 
   \section{Simulating Fractional L\'evy Motion}\label{section:sFLM}
-
-  \subsection{Truncated L\'evy stable hop distributions}\label{section:truncation}
-
-  \textit{Determining where to truncate the hop distribution:} A pure
-  L\'evy stable distribution has heavy tails which can lead to arbitrarily
-  long hop lengths. Our distribution of hop lengths fits well to a L\'evy
-  distribution near the mean, but under samples the tails. In 
-  Figure~\ref{fig:truncation_correction} we compare the empirically 
-  measured transition emission distribution of the MSDDM for Urea to its maximum likelihood fit to
-  a L\'evy stable distribution. The ratio between the two distributions 
-  at each bin is nearly 1 close to the center, indicating a near-perfect
-  fit, larger than 1 slightly further from the center, suggesting that 
-  we slightly over sample intermediate hop lengths, and below 1 far from 
-  the center, indicating under sampling of extremely long hop lengths.
-  Based on the plot, we chose a cut-off of 0.8 nm in order to compensate for
-  over sampled intermediate hop lengths. We used the same procedure
-  to determine truncation parameters for all solutes.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.75\textwidth]{truncation_cutoff.pdf}
-  \caption{The ratio between the empirical and maximum likelihood theoretical
-  distribution quantifies the quality of fit as function of hop length. The fit
-  is near-perfect close to the mean. Intermediate hop lengths are over sampled, 
-  and the tails are under sampled. We used this type of plot to determine the
-  appropriate place to truncate the L\'evy stable distributions.}\label{fig:truncation_cutoff}
-  \end{figure}
-
-  \textit{Generating FLM realizations from a truncated L\'evy distribution:}
-  To generate realizations from an uncorrelated truncated L\'evy process, one would
-  randomly sample from the base distribution and replace values that are too large
-  with new random samples from the base distribution, repeating the process until
-  all samples are under the desired cut-off.
-
-  This procedure is complicated by the correlation structure of FLM. At a high level,
-  Stoev and Taqqu use Riemann-sum approximations of the stochastic integrals defining
-  FLM in order to generate realizations. They do this efficiently with the help of 
-  Fast Fourier Transforms. In practice, this requires one to Fourier transform a zero-padded
-  vector of random samples drawn from the appropriate L\'evy stable distribution, multiply
-  the vector in Fourier space by a kernel function and invert back to real space. The end
-  result is a correlated vector of fractional L\'evy noise.
-
-  If one is to truncate an FLM process, one can apply the simple procedure above for 
-  drawing uncorrelated values from the marginal L\'evy stable distribution, but after
-  adding correlation, the maximum drawn value is typically lower than the limit set 
-  by the user. Additionally, the shape of the distribution itself changes. Analogous
-  to the database used to correct the Hurst parameter, we created a database to 
-  correct the input truncation parameter (the maximum desired draw). The database
-  returns the value of the truncation parameter that will properly truncate the
-  output marginal distribution based on $H$, $\alpha$ and $\sigma$ (the width parameter).
-  Figure~\ref{fig:truncation_correction} shows the result of applying our correction.
-  Note that generating this database requires a significant amount of simulation and
-  still likely doesn't perfectly correct the truncation parameter. The output leads
-  to a somewhat fuzzy, rather than abrupt, cut-off of the output distribution. This 
-  is likely beneficial since we observe a small proportion of hops longer the chosen
-  truncation cut-off. When the cut-off value is close to the L\'evy stable $\sigma$ parameter,
-  as it is in our anomalous diffusion models, we observed that the tails of the 
-  truncated distribution tend to be undersampled. In order to maintain the distribution's 
-  approximate shape up to the cut-off value we recommend ensuring that the cut-off
-  value is at least 2 times $\sigma$. However, this may lead to a slight over-prediction
-  of the MSD.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{truncation_correction.pdf}
-  \caption{We can accurately truncate the marginal distribution of FLM innovations by
-  applying a correction to the input truncation parameter. We generated FLM sequences
-  and truncated the initial L\'evy stable distribution (before Fourier transforming) at 
-  a value of 0.5. After correlation structure is added, the width of the distribution 
-  of fractional L\'evy noise decreases significantly. We corrected the input truncation
-  parameter with our database resulting in a distribution close to the theoretical
-  distribution (black dashed line) with a maximum value close to 0.5.}\label{fig:truncation_correction}
-  \end{figure}
 
@@
   \end{figure}
+
+  \subsection{Truncated L\'evy stable hop distributions}\label{section:truncation}
+
+  \textit{Determining where to truncate the hop distribution:} A pure
+  L\'evy stable distribution has heavy tails which can lead to arbitrarily
+  long hop lengths. Our distribution of hop lengths fits well to a L\'evy
+  distribution near the mean, but under samples the tails. In 
+  Figure~\ref{fig:truncation_correction} we compare the empirically 
+  measured transition emission distribution of the MSDDM for urea to its maximum likelihood fit to
+  a L\'evy stable distribution. The ratio between the two distributions 
+  at each bin is nearly 1 close to the center, indicating a near-perfect
+  fit, larger than 1 slightly further from the center, suggesting that 
+  we slightly over sample intermediate hop lengths, and below 1 far from 
+  the center, indicating under sampling of extremely long hop lengths.
+  Based on the plot, we chose a cut-off of 1 nm in order to compensate for
+  over sampled intermediate hop lengths. We chose the same cut-off for all
+  solutes.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.75\textwidth]{truncation_cutoff.pdf}
+  \caption{The ratio between the empirical and maximum likelihood theoretical
+  distribution quantifies the quality of fit as function of hop length. The fit
+  is near-perfect close to the mean. Intermediate hop lengths are over sampled, 
+  and the tails are under sampled. We used this type of plot to determine the
+  appropriate place to truncate the L\'evy stable distributions.}\label{fig:truncation_cutoff}
+  \end{figure}
+
+  \textit{Generating FLM realizations from a truncated L\'evy distribution:}
+  To generate realizations from an uncorrelated truncated L\'evy process, one would
+  randomly sample from the base distribution and replace values that are too large
+  with new random samples from the base distribution, repeating the process until
+  all samples are under the desired cut-off.
+
+  This procedure is complicated by the correlation structure of FLM. At a high level,
+  Stoev and Taqqu use Riemann-sum approximations of the stochastic integrals defining
+  FLM in order to generate realizations.~\cite{stoev_simulation_2004} They do this efficiently with the help of 
+  Fast Fourier Transforms. In practice, this requires one to Fourier transform a zero-padded
+  vector of random samples drawn from the appropriate L\'evy stable distribution, multiply
+  the vector in Fourier space by a kernel function and invert back to real space. The end
+  result is a correlated vector of fractional L\'evy noise.
+
+  We are unaware of a technique for simulating truncated FLM, therefore we devised our
+  own based on the above discussion. If one is to truncate an FLM process, one can apply
+  the simple procedure above for drawing uncorrelated values from the marginal L\'evy 
+  stable distribution, \textit{but}, after adding correlation, the maximum drawn value is typically lower than the limit set 
+  by the user. Additionally, the shape of the distribution itself changes. Therefore, 
+  we created a database meant to correct the input truncation parameter (the maximum desired draw). The database
+  returns the value of the truncation parameter that will properly truncate the
+  output marginal distribution based on $H$, $\alpha$ and $\sigma$ (the width parameter).
+  Figure~\ref{fig:truncation_correction} shows the result of applying our correction.
+  Note that generating this database requires a significant amount of simulation and
+  still likely doesn't perfectly correct the truncation parameter. The output leads
+  to a somewhat fuzzy, rather than abrupt, cut-off of the output distribution. This 
+  is likely beneficial since we observe a small proportion of hops longer the chosen
+  truncation cut-off. When the cut-off value is close to the L\'evy stable $\sigma$ parameter,
+  as it is in our anomalous diffusion models, we observed that the tails of the 
+  truncated distribution tend to be undersampled. In order to maintain the distribution's 
+  approximate shape up to the cut-off value we recommend ensuring that the cut-off
+  value is at least 2 times $\sigma$. However, this may lead to a slight over-prediction
+  of the MSD.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{truncation_correction.pdf}
+  \caption{We can accurately truncate the marginal distribution of FLM innovations by
+  applying a correction to the input truncation parameter. We generated FLM sequences
+  and truncated the initial L\'evy stable distribution (before Fourier transforming) at 
+  a value of 0.5. After correlation structure is added, the width of the distribution 
+  of fractional L\'evy noise decreases significantly. We corrected the input truncation
+  parameter with our database resulting in a distribution close to the theoretical
+  distribution (black dashed line) with a maximum value close to 0.5.}\label{fig:truncation_correction}
+  \end{figure}
+
+  \newpage
 
@@
 
+  \newpage
+
   \section{Derivation of Passage Time Distributions}\label{section:fpt_derivation}
 
-  To derive an analytical equation for the mean first passage time as calculated
-  in the main text, first consider an initial pulse spreading out over time with
-  a fixed mean. We can solve for the time-dependent probability density of 
-  particle positions by solving the one dimensional diffusion equation:
+  To derive an analytical equation for the mean first passage time 
+  (Equation~\ref{M-eqn:passage_times} of the main text), first consider an 
+  initial pulse spreading out over time with a fixed mean. We can solve for the 
+  time-dependent probability density of particle positions, $p$, by solving the one
+  dimensional diffusion equation:
   \begin{equation}
@@
   where the only free parameters for fitting are $v$ and $D$. We calculated the
-  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT.
+  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT. Specifically,
+  we used the python package \texttt{scipy.integrate.quad} to numerically integrate:
+  \begin{equation}
+  E[t] = \int_0^\infty tP(t) dt
+  \end{equation}
+
+  \newpage
 
@@
 
-  \begin{figure}
+  Analagous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
+  Figures~\ref{fig:GCL_anticorrelated_hops}--\ref{fig:MET_anticorrelated_hops} 
+  demonstrate that all solutes exhibit the same kind of anti-correlated hopping
+  and trapping behavior.
+
+  \begin{figure}[h]
   \centering
@@
   \caption{For ethylene glycol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
-  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
-  for ethylene glycol. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
+  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions. 
+  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
   in the main text for a more detailed discussion.}\label{fig:GCL_anticorrelated_hops}
@@
   \caption{For acetic acid: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
-  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
-  for acetic acid. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
+  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions.
+  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
   in the main text for a more detailed discussion.}\label{fig:ACH_anticorrelated_hops}
@@
   \caption{For methanol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
-  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
-  for methanol. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
+  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions.
+  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
   in the main text for a more detailed discussion.}\label{fig:MET_anticorrelated_hops}
@@
 
+  \newpage
+
+  \section{Stationarity of Solute Trajectories}\label{section:msd_comparison}
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
+  \caption{Urea}\label{fig:URE_MSD_halves}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
+  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
+  \caption{Methanol}\label{fig:MET_MSD_halves}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
+  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
+  \end{subfigure}
+  \caption{The ensemble of solute trajectories may be stationary if the MSD
+  calculated from different portions of the trajectory are the same. Here we
+  plot the MSD calcluated up to a 500 ns time lag of the first and second
+  halves of the equilibrated solute trajctories. Urea and acetic acid have
+  similar MSDs, providing evidence of stationarity, while the MSDs of 
+  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
+  \end{figure}
+
+  \newpage
+
   \section{Tabular Anomalous Diffusion Parameters}\label{section:tabular_AD_params}
+
+  The tables in the section are tabular representations of the parameters depicted
+  in Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the 
+  main text.
 
@@
 
-  \section{Stationarity of Solute Trajectories}\label{section:msd_comparison}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
-  \caption{Urea}\label{fig:URE_MSD_halves}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
-  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
-  \caption{Methanol}\label{fig:MET_MSD_halves}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
-  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
-  \end{subfigure}
-  \caption{The ensemble of solute trajectories may be stationary if the MSD
-  calculated from different portions of the trajectory are the same. Here we
-  plot the MSD calcluated up to a 500 ns time lag of the first and second
-  halves of the equilibrated solute trajctories. Urea and acetic acid have
-  similar MSDs, providing evidence of stationarity, while the MSDs of 
-  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
-  \end{figure}
+  \newpage
 
   \section{Tabular MSDDM parameters}\label{section:msddm_params}
+
+  The following table is a tabular representation of the parameters 
+  depicted in Figure~\ref{M-fig:msddm_parameters} of the main text.
 
@@
 
-  \section{2-state MSDDM parameters}\label{section:simple_msddm_params}
+% This is not used I think
+%  \section{2-state MSDDM parameters}\label{section:simple_msddm_params}
+%  
+%  We used a simple 2-state model to illustrate how the self-transition probability 
+%  effects simulated MSDs generated from the MSDDM. We used the following parameters:
+%  
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{|c|c|c|c|}
+%  \hline
+%  State & H     & $\alpha_h$ & $\sigma$ \\\hline
+%  1     & 0.1  & 1.7       & 0.04    \\
+%  2     & 0.2  & 1.5       & 0.04    \\
+%  T     & 0.4  & 1.4       & 0.04    \\\hline
+%  \end{tabular}
+%  \caption{Values of $H$, $\alpha_h$ and $\sigma$ used to simulate realizations
+%  of the simple MSDDM whose MSDs are shown in Figure~\ref{M-fig:T_sensitivity} of
+%  the main text. The values are chosen to be similar to those in Table~\ref{M-table:msddm_params}
+%  of the main text.}\label{table:msddm_params}
+%  \end{table}
 
-  We used a simple 2-state model to illustrate how the self-transition probability 
-  effects simulated MSDs generated from the MSDDM. We used the following parameters:
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{|c|c|c|c|}
-  \hline
-  State & H     & $\alpha_h$ & $\sigma$ \\\hline
-  1     & 0.1  & 1.7       & 0.04    \\
-  2     & 0.2  & 1.5       & 0.04    \\
-  T     & 0.4  & 1.4       & 0.04    \\\hline
-  \end{tabular}
-  \caption{Values of $H$, $\alpha_h$ and $\sigma$ used to simulate realizations
-  of the simple MSDDM whose MSDs are shown in Figure~\ref{M-fig:T_sensitivity} of
-  the main text. The values are chosen to be similar to those in Table~\ref{M-table:msddm_params}
-  of the main text.}\label{table:msddm_params}
-  \end{table}
+  \newpage
 
@@
 
-  \begin{figure}
+  In Figures~\ref{fig:ad_fpt_fits} and~\ref{fig:msddm_fpt_fits}, we demonstrate
+  the high quality of our analytical fits of Equation~\ref{eqn:passage_times} to 
+  the distribution of solute first passage times derived from both the AD
+  and MSDDM models. The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
+  relatively noisy because we only generated 1000 realizations of the MSDDM 
+  versus 10000 of the AD model. In Figure~\ref{fig:flux_curve_sensitivity}, we
+  justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
+  model realizations to show that one needs as few as 100 independent trajectory
+  realizations at each pore length in order to reliably fit Equation~\ref{eqn:passage_times}
+  to the passage time distributions.
+
+  \begin{figure}[h]
   \centering

### 2020-01-01 Ben_Manuscripts/stochastic_transport/figures/mfpt_curve.py

@@ -189,8 +189,7 @@ else:
     fig1.savefig('flux_curves_brownian.pdf')
     fig2.savefig('mfpt_curves_brownian.pdf')
     plt.show()
-    exit()
-exit()
+
 ####################
 # Selectivity Plot #
 ####################
@@ -216,6 +215,9 @@ plt.legend(fontsize=12)
 plt.xlabel('Pore length ($\mu m$)', fontsize=14)
 plt.ylabel('Selectivity', fontsize=14)
 plt.tick_params(labelsize=14)
+if msddm:
+	plt.ylim(0, 4)
+
 plt.tight_layout()
 if msddm:
     plt.savefig('selectivity_msddm.pdf')

### 2020-01-03 Ben_Manuscripts/stochastic_transport/Draft.tex
Updates to figures

@@
 
+\usepackage{setspace}
+\doublespacing
 \usepackage{multirow}
@@
 
-%MRS4: Overall - providing a bit gentler easing into the modeling would help.
-A more clearly articulated overall picture of what the goals of the modeling are.
-Does it have to be perfect?
-Is the main goal just predictive time series, or mechanistic understanding?
-Help people a bit more to understand what success or failure would look like.
-Help make it clear why the specific models are chosen to investigate.
-%MRS4: To what extent can findings be related back to molecular details?
-%MRS4: what are the consequences of the findings?
-
+%BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
 \title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
 and Predicts Long Timescale Behavior in Nanoscale Pores.}
-%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
-%MRS4: can we turn this into a thesis statement (we find X) rather than a topic statement (we studied X).  Something about the complexity of the models required to get the subdiffusive behavior right?
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   allow us to predict solute MSDs. We show that our models reasonably reproduce
-  MSDs calculated from MD simulations. The anomalous diffusion model shows 
-  superior predictive performance, in many cases reproducing MD results well
-  within error. Finally, we demonstrate how one can use our models in order to
-  calculate flux of a given solute across a macroscopic-length pore and, based on 
-  those quantities, the membrane's selectivity towards each solute. Overall, this
-  work helps connect the relationship between microscopic chemically-dependent
-  solute motions and macroscopic membrane performance.
+  the MSDs calculated from MD simulations. Finally, we demonstrate how one can
+  use our models in order to calculate flux of a given solute across a 
+  macroscopic-length pore and, based on those quantities, the membrane's selectivity
+  towards each solute. Overall, this work helps connect the relationship between
+  microscopic chemically-dependent solute motions and macroscopic membrane performance.
 
@@
   and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
-  %BJC4: made more general. 
+  %BJC5: made more general. 
   there is a strong interest in creating breathable fabrics % barriers 
@@
 
-  In this work, we use the output of our MD simulations to construct two new classes of 
+  In this work, we use the output of our MD simulations to construct two classes of 
   mathematical models which aim to predict membrane performance while providing quantitative 
@@
   single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
-  %BJC4: consider rewording sentence below
   A CTRW is characterized by a distribution of hop lengths and dwell times, 
@@
   We extend the framework to include state-dependent fluctuations and correlations in 
-  solute position. The magnitudes of a solute's fluctuations from its average trapped 
-  position and the degree of correlation with its previous fluctuations is 
+  solute position. The magnitude of solute fluctuations from its average trapped 
+  position and the degree of correlation with previous fluctuations is 
   determined by the current state. To distinguish our approach from standard MSMs, we have
@@
 
-  Finally, we use our most promising model in order to predict solute flux and 
-  selectivity in pores of macroscopic length, thus achieving a better understanding
+  Finally, we use both models in order to predict solute flux and selectivity in 
+  pores of macroscopic length, thus achieving a better understanding
   of macroscopic properties on the basis of microscopic dynamics. We show that 
@@
   mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
-  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 0$ 
+  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
   are characteristic of Brownian and superdiffusive motion respectively.
@@
   In a pure CTRW, for example, the power law distribution of trapping times leads to
-  weak ergodicity breaking. The time-averaged MSD is linear while the ensemble averaged
+  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
   MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
@@
   are so close to zero. Therefore, we obtained H by performing a least squares fit of 
-  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 400 ps time lags of the 
+  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 0.5 ns time lags of the 
   empirically measured autocorrelation function.
@@
   % BJC3: will need to modify this text to reflect different lengths of simulations
-  For each solute, we simulated 10,000 anomalous diffusion trajectories of length
+  For each solute, we simulated 1,000 anomalous diffusion trajectories of length
   $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
@@
   %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
-  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
-  with corresponding 95\% confidence intervals.
+  We reported the time-averaged MSD up to a 1000 ns time lag corresponding 95\% confidence
+  intervals.
+
   When simulating 2 mode models, we determined the state sequence based on random 
-  draws weighted by the appropriate row of the probability transition matrix. We 
+  draws weighted by the appropriate row of the probability transition matrix. We then
   drew hops and dwells based on the current state of the system. Since we calculated
@@
 
-  %We also projected MSDs out to 1 second for each solute. % BJC3:??
   %BJC3: not sure how to cite fbm
@@
   we used sufficiently approximates draws from the marginal distribution and 
-  reasonably approximates the correlation structure. We added an empirical correction
-  to enhance the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
-  of the Supporting Information for validation of the approach).
+  reasonably approximates the correlation structure on MD simulation timescales. We
+  added an empirical correction to enhance the accuracy of the correlation structure
+  (see Section~\ref{S-section:flm_correlation} of the Supporting Information for 
+  validation of the approach).
 
@@
 
-  % BJC3: This explanation is in previous section
-  %For example, if 
-  %we observed state 1 followed by a transition to state 3, we increment the $(1, 3)$ entry
-  %of the count matrix by 1. We generate the transition probability matrix from the count matrix by 
-  %normalizing the entries in each row so that they summed to unity.
-
   Adding to the standard MSM framework, we incorporated the dynamics of the solutes
@@
   While MSMs are often used to estimate equilibrium populations of various states, adding 
-  state-dependent dynamics allows us to more accurately simulate solute trajectories.
-  %BJC4: I said below already
-  Hence we distinguish our model from MSMs by referring them as Markov State-Dependent
-  Dynamical Models (MSDDMs).
+  state-dependent dynamics allows us to simulate solute trajectories.
+  %BJC5: I said below already, but I still think it belongs
+  Hence why we refer to them as Markov State-Dependent Dynamical Models (MSDDMs).
 
@@
   However, there is not sufficient data to accurately measure a Hurst parameter for 
-  each type of transition. We avoided this problem by treating transitions as correlated
+  each type of transition. We avoided this problem by combining all distributions 
+  associated with state transitions and treating all transitions as correlated
   emissions from a single L\'evy stable distribution. This reduces the number of emission
@@
   to construct a distribution of first passage times across a membrane pore of length $L$.
-  We simulated 50000 trajectory realizations, released at the pore entrance ($z=0$). In the case of 
+  For computational reasons dependent on the model used, we simulated 1000-10000 trajectory
+  realizations, released at the pore entrance ($z=0$). In the case of 
   uncorrelated hops, one can continuously draw from the hop length distribution until 
@@
   To come up with an analytical equation describing the passage time distributions, 
-  one can frame the problem as a pulse of particles instantaneously released at the 
-  pore inlet ($z=0$) which moves at a constant velocity, $v$, and spreads out as it 
-  approaches $L$. This spreading is parameterized by an effective diffusivity 
-  parameter, $D$. This approach gives results equivalent to if we had released each
-  particle individually and then analyzed the positions of the ensemble of trajectories as 
+  one can frame the 
+  problem as a pulse of particles instantaneously released at the pore inlet ($z=0$)
+  which moves at a constant velocity, $v$, and spreads out as it approaches $L$. 
+  This spreading is parameterized by an effective diffusivity parameter, $D$. This 
+  approach gives results equivalent to if we had released each particle individually
+  and then analyzed the positions of the ensemble of trajectories as 
   a function of time. The analytical expression describing the distribution of 
@@
   anti-correlation between hops suggests a fractional diffusion process is subordinate to the
-  CTRW. We believe the subordinated process is FBM because its analytical correlation 
-  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
-  is common in crowded viscoelastic environments where motions are highly influenced by
-  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
+  CTRW. We believe the subordinated process is FBM or FLM because their analytical correlation 
+  structures are close to those observed in our simulations (Figure~\ref{fig:hop_acf}). Fractional
+  motion is common in crowded viscoelastic environments where movement is highly influenced by
+  the movement of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
   %The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
@@
   hop. In combination, (a) -- (d) support modeling solutes as subordinated fractional Brownian
-  motion. The behavior shown by urea in this figure is common to all solutes in this study (see
+  and L\'evy motion. The behavior shown by urea in this figure is common to all solutes in this study (see
   Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops} of the
@@
 
+  Realizations of the AD model based on the parameterization procedures just described
+  yield qualitatively similar trajectories to those seen in our MD simulations. In
+  Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for each
+  combination of the dwell time and hop distribution, labeled according to Table~\ref{table:anomalous_models}.
+  The sFBMcut and sFLMcut in particular resemble the trajectories in Figure~\ref{fig:solute_trajectories}.
+  When we do not truncate the dwell time distribution, the trajectories tend to 
+  incorporate very long dwell times as shown by the sFBM and sFLM models.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{ad_realizations_1mode.pdf}
+  \caption{Simulations of 1 mode AD model trajectories for Urea display qualitatively
+  similar hopping and trapping behavior to that shown in Figure~\ref{fig:solute_trajectories}. 
+  Dwell times appear exaggerated in the sFBM and sFLM models because the power law dwell
+  time distributions are not truncated and have infinite variance.
+  %Analogous plots are shown for other solutes
+  %BJC5: todo: add plots to SI. Show I add a 2 mode model plot?
+  %and the 2 mode model in the Supporting Information. 
+  }\label{fig:ad_eyetest}
+  \end{figure}
+
   \subsubsection{Model validation on stationary trajectories}\label{section:sfbm_validation}
@@
   for each solute based on the time at which the number of solutes inside the
-  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
+  pores and tails stabilized (Figure~\ref{S-fig:equilibration}). Nonetheless, we observe evidence of non-stationary
   solute behavior after equilibration, on the $\mu$s timescale. In Table~\ref{table:stationarity},
   we compare the MSD of the solutes calculated using trajectory data from the 
-  first and second halves of the equilibrated simulation time. Ethylene glycol 
+  first and second halves of the ``equilibrated" simulation time. Ethylene glycol 
   and methanol show considerable differences in their MSDs. Urea and acetic acid
@@
   Using the approach described above, we validated our 1 and 2 mode models with
-  urea and acetic acid, since their trajectories appear stationary. In 
-  Figure~\ref{fig:ad_eyetest}, we show that realizations of the AD model appear
-  qualitatively similar to those seen in our MD simulations (Figure~\ref{fig:solute_trajectories}).
+  urea and acetic acid, since their trajectories appear stationary. 
   The MSDs resulting from 1000 realizations of the AD model are shown in 
   Figure~\ref{fig:train_test}. We consider the model's prediction to match well if the
-  MSD lies within the 1-$\sigma$ confidence intervals of the MD MSDs. We also
+  MSD lies within the 1$\sigma$ confidence intervals of the MD MSDs. We also
   look for qualitative agreement in the shape of the curves.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{ad_realizations_1mode.pdf}
-  \caption{Simulations of 1 mode AD model trajectories for Urea display 
-  qualitatively similar hopping and trapping behavior to that shown in 
-  Figure~\ref{fig:solute_trajectories}. Analogous plots are shown for other solutes
-  %BJC5: todo: add plots to SI. Show I add a 2 mode model plot?
-  and the 2 mode mdoel in the Supporting Information. Dwell times may be exaggerated in the
-  sFBM and sFLM models because the power law dwell time distributions have infinite
-  variance.}\label{fig:ad_eyetest}
-  \end{figure}
 
@@
   (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
-  the first half of the equilibrated data lie within the 1-$\sigma$ confidence
+  the first half of the equilibrated data lie within the 1$\sigma$ confidence
   intervals of the MD MSD curves generated from the second half of the equilibrated
   solute data. The models which use pure power laws systematically under-predict
-  the MD MSD curves. The shape of the MSD curves appear qualitatively correct
-  for urea, but lack curvature in the case of acetic acid.}\label{fig:train_test}
+  the MD MSD curves. Improper curvature of the MSD curves cause the magnitude of
+  the urea's predicted MSDs to be under-predicted at long timescales and those
+  of acetic acid to be under-predicted at short timescales.}\label{fig:train_test}
   \end{figure}
@@
 
-  This brief qualitative analysis suggests two shortcomings of the AD model. First, 
-  positional anti-correlation may dissipate after a sufficiently long time lag, dependent on the 
-  solute being studied. Second, it is difficult to reliably parameterize the Hurst
-  parameter which is important for accurately describing the curvature of the solute
-  MSDs.
+  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
+  a real system, positional anti-correlation may dissipate after a sufficiently long 
+  time lag, dependent on the solute being studied. Second, it is difficult to reliably
+  parameterize the Hurst parameter which is important for accurately describing the 
+  curvature of the solute MSDs.
 
@@
   We obtain reasonable predictions of the MD simulated MSDs when we parameterize the AD 
-  model with all available data after the perceived equilibration time. We visualized the
-  parameters in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
+  model with all available data after the perceived equilibration time. Although we 
+  concluded that methanol and ethylene glycol trajectories are not yet stationary, we 
+  include them in all analysis going forward because it is still instructive. 
   The MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
   comparison in Figures~\ref{fig:anomalous_msds_1mode} and~\ref{fig:anomalous_msds_2mode}
-  respectively. Although we concluded that methanol and ethylene glycol trajectories are
-  not yet stationary, we include them in all analysis going forward because it is still
-  instructive.
+  respectively. The associated parameters are presented in Figures~\ref{fig:1mode_parameters}
+  and~\ref{fig:2mode_parameters}.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE.pdf}
+  \caption{Urea}\label{fig:1mode_msd_comparison_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_GCL.pdf}
+  \caption{Ethylene Glycol}\label{fig:1mode_msd_comparison_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_MET.pdf}
+  \caption{Methanol}\label{fig:1mode_msd_comparison_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:1mode_msd_comparison_ACH}
+  \end{subfigure}
+  \caption{In most cases, MSDs generated from realizations of our 1 mode anomalous
+  lie within or near the 1$\sigma$ confidence intervals of MD-generated data when using an
+  exponential cutoff on the dwell time distribution (sFBMcut and SFLMcut). When we
+  do not apply an exponential cut-off (sFBM and SFLM), MSDs are underpredicted. 
+  Drawing hops from a truncated L\'evy stable distribution yields MSDs similar to 
+  when hops are drawn from Gaussian disributions (sFLM and sFLMcut). In most 
+  cases, the MSDs are under-predicted at long timescales because the AD models
+  show pronounced curvature which the MD simulations lack.}\label{fig:anomalous_msds_1mode}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE.pdf}
+  \caption{Urea}\label{fig:2mode_msd_comparison_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_GCL.pdf}
+  \caption{Ethylene Glycol}\label{fig:2mode_msd_comparison_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_MET.pdf}
+  \caption{Methanol}\label{fig:2mode_msd_comparison_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:2mode_msd_comparison_ACH}
+  \end{subfigure}
+  \caption{MSDs generated from realizations of our 2-mode anomalous diffusion model
+  predict the magnitude of the MSDs to a similar degree of accuracy as the 1 mode
+  model. Relative to the predictions of the 1 mode model the MSDs lack curvature because
+  the hop correlation structure is broken every time a transition between tails occurs.}\label{fig:anomalous_msds_2mode}
+  \end{figure}
 
@@
 
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE.pdf}
-  \caption{Urea}\label{fig:1mode_msd_comparison_URE}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_GCL.pdf}
-  \caption{Ethylene Glycol}\label{fig:1mode_msd_comparison_GCL}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_MET.pdf}
-  \caption{Methanol}\label{fig:1mode_msd_comparison_MET}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH.pdf}
-  \caption{Acetic Acid}\label{fig:1mode_msd_comparison_ACH}
-  \end{subfigure}
-  \caption{In most cases, MSDs generated from realizations of our 1 mode anomalous
-  diffusion models agree well with MD-generated data when using an exponential cutoff
-  on the dwell time distribution (sFBMcut and SFLMcut). When we do not apply an 
-  exponential cut-off (sFBM and SFLM), MSDs are underpredicted. Drawing hops from a
-  truncated L\'evy stable distribution yields MSDs similar to when hops are drawn 
-  from Gaussian disributions (sFLM and sFLMcut).}\label{fig:anomalous_msds_1mode}
-  \end{figure}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE.pdf}
-  \caption{Urea}\label{fig:2mode_msd_comparison_URE}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_GCL.pdf}
-  \caption{Ethylene Glycol}\label{fig:2mode_msd_comparison_GCL}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_MET.pdf}
-  \caption{Methanol}\label{fig:2mode_msd_comparison_MET}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH.pdf}
-  \caption{Acetic Acid}\label{fig:2mode_msd_comparison_ACH}
-  \end{subfigure}
-  \caption{MSDs generated from realizations of our 2-mode anomalous diffusion model
-  predict the magnitude of the MSDs to a similar degree of accuracy as the 1 mode
-  model. Relative to the predictions of the 1 mode model the MSDs lack curvature because
-  the hop correlation structure is broken every time a transition between tails occurs.}\label{fig:anomalous_msds_2mode}
-  \end{figure}
-
   After a 1000 ns time lag, the 1 and 2 mode AD models do a fairly good job of 
@@
   and sFLMcut models give very similar results probably because their $\alpha_h$
-  parameter values are relatively close to 2, meaning the hop length distribution
-  is nearly Gaussian even when fit to a more general L\'evy distribution.
+  parameter values are relatively close to 2, meaning the hop length distributions
+  are nearly Gaussian even when fit to a more general L\'evy distribution.
 
@@
   this point. At first glance, acetic acid's predicted MSD (sFLMcut and sFBMcut)
-  appear to match the curvature of MD quite well, but closer examination reveals
+  appears to match the curvature of MD quite well, but closer examination reveals
   that the MD MSD curve actually shifts from a sub-linear to a linear regime 
@@
   are fairly stable in both regions since they are small and hydrophilic. Ethylene 
-  glycol is has a slight preference for the pores likely because it is a larger
+  glycol has a slight preference for the pores likely because it is a larger
   molecule with two hydrophilic hydroxyl groups.}\label{fig:AD_mode_occupation}
@@
 
-  \subsection{Markov State-Dependent Dynamics}\label{section:msm_results}
+  \subsection{The Markov State-Dependent Dynamical Model}\label{section:msm_results}
 
@@
   significant portion of time hydrogen bonded while in the tail regions.
-  Most of the tail region hydrogen bonds are donated from methanol to the ether
-  linkages between the monomer head groups and tails.
+  Tail region hydrogen bonds are donated from methanol to the ether linkages between
+  the monomer head groups and tails.
 
@@
   In theory, one could parameterize separate transition distributions for those
-  which occur in the tails versus in the pores, however this would lead a broken 
+  which occur in the tails versus in the pores, however this would lead to a broken 
   correlation structure similar to that seen in the 2 mode AD model.
@@
   The largest hops occur when solutes are unbound in the pores. (c) The weight of the 
-  hop length distribution's tails, parameterized by $\alpha_h$ increases as more trapping
-  mechanisms influence solute simultaneously. The transition hop distributions have
+  hop length distribution's tails, parameterized by $\alpha_h$, increases as more trapping
+  mechanisms influence solutes simultaneously. The transition hop distributions have
   among the heaviest tails.}\label{fig:msddm_parameters}
@@
   hop length distributions are much smaller than those of the AD model. Closer
-  examination of Figure~\ref{fig:solute_trajectories} reveals that hops tend
-  to be an accumulation of a series of hops in the same direction. All of the 
-  hops in the MSDDM are negatively correlated which prevents this from happening.
+  examination of urea's MD trajectories shown in Figure~\ref{fig:solute_trajectories} 
+  reveal that hops tend to be an accumulation of a series of hops in the same direction.
+  All of the hops in the MSDDM are negatively correlated which prevents this from happening.
   The second reason is a consequence of using a single hop length distribution 
@@
   MSDDM agree well with those generated from MD simulations. The predicted MSD
-  curves of urea and ethylene glycol lie within the 1-$\sigma$ confidence 
+  curves of urea and ethylene glycol lie within the 1$\sigma$ confidence 
   intervals of MD for all time lags. Methanol over-predicts the MSD at small
@@
   Figure~\ref{fig:msddm_performance}). In most cases, the MSDDM predicts the magnitude of the MD MSDs 
-  within their 1-$\sigma$ confidence intervals. One could argue that the curves
+  within their 1$\sigma$ confidence intervals. One could argue that the curves
   of ethylene glycol and urea are statistically indistinguishable. However, 
@@
   due to displacements during state transitions. Acetic acid has a transitional
-  Hurst parameter close to Urea's and a transitional $\sigma$ value that 
+  Hurst parameter close to urea's and a transitional $\sigma$ value that 
   is higher than urea's. This suggests that the heavier tails of urea's transitional
   hop distribution (greater $\alpha_h$ value) are in large part responsible for 
-  urea's higher predicted MSD. Although we note that acetic acid's predicted MSD
-  actually lies just within the lower bound of Urea's MD MSD 1-$\sigma$ 
+  urea's higher predicted MSD. Although, note that acetic acid's predicted MSD
+  actually lies just within the lower bound of Urea's MD MSD 1$\sigma$ 
   confidence interval. There is also the strong possibility that the over-estimate is
@@
   in most cases, it is the source of qualitative mismatches between MSDDM
-  realations and MD simulation trajectories and it may be the source of the 
+  realizations and MD simulation trajectories and it may be the source of the 
   over-estimate of acetic acid's MSD.
@@
   in order to calculate the flux (see section~\ref{method:mfpt}) of solutes given model 
-  parameters extracted from MD simulations. The 1-mode sFBMcut mode generates predictions
+  parameters extracted from MD simulations. The 1-mode sFBMcut model generates predictions
   similar to the 1-mode sFLMcut model at a lower computational cost and is far more
-  accurate than sFBM and sFLM. The 2-mode AD model has a broken correlation structure, 
-  so we do not consider it here.
+  accurate than sFBM and sFLM. We showed that the 2-mode AD model has a broken correlation
+  structure, so we do not consider it here.
 
@@
   in the AD models, the $\beta$ parameter is only a function of $H$ and not dependent on
-  dwell times ($\alpha_d$) or hop lengths ($\sigma$). The MSDDM is fundamentally similar to 
+  dwell times ($\alpha_d$, $\lambda$) or hop lengths ($\sigma$). The MSDDM is fundamentally similar to 
   the AD model in that one makes correlated draws from a hop distribution. Therefore,
@@
   The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
-  itself as well as inaccuracies resulting from of simulation of very long FLM trajectories.
+  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
   Turning first to the model itself, we have designed it to ensure that the magnitude of the
@@
   must initialize a new time series sub-trajectory with its own correlation structure. 
-  Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
-  in each state is relatively short making the accuracy of the correlation structure 
-  questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
-  $\sigma$ in trapped states. Since we add the transitional hop lengths to each end of
+  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
+  %in each state is relatively short making the accuracy of the correlation structure 
+  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
+  %$\sigma$ in trapped states. 
+  Since we add the transitional hop lengths to each end of
   trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
-  to one another largely decorrelating them. We tested this reasoning by modifying the 
+  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
   MSDDM to completely immobilize particles except when they transition between states. 
@@
   FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
+  To generate the curves in Figure~\ref{fig:flux_curves_msddm}, we needed to correlate 
+  25--1000 times more hops than for the MSD predictions in Figure~\ref{fig:msddm_performance}. 
   In short, it is computationally infeasible to use enough terms to accurately incorporate
@@
   fractional Brownian motion, for which we have an exact simulation method, in place of 
-  FLM. When we use FBM, $\beta$ increases well above the Brownian value. $\beta$ increases
-  even further if we immobilize the trapped states. Thus the low value of $\beta$ of the
-  MSDDM is a consequence of model assumptions and inexact simulation of FLM.
+  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
+  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
+  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
+  of FLM.
 
@@
   \end{subfigure}
+  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
   \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
@@
 
-  The values of $c$ are likely a complex function of $\sigma$, $alpha_d$, $H$ and $\alpha_d$
-  where applicable. The values of $c$ scale the flux curves and are directly correlated to 
-  flux magnitude. We showed earlier that $\beta$ is not a function of $\sigma$ or $\alpha_d$,
-  therefore dwell times and hop lengths must influence $c$. In fact, any parameter which acts
-  to modify the rate at which solutes move through the membrane pores will affect $c$.
-  Therefore it is sensible to hypothesize that a higher degree of anti-correlation (lower $H$)
-  should decrease $c$ and a higher value of $\alpha_h$ should also increase $c$.
+  The values of $c$ are directly related to the magnitude of solute flux and, where
+  applicable, are functions of $\sigma$, $\alpha_d$, $\lambda$ and $\alpha_h$. 
+  In Figure~\ref{fig:c_parameters}, we plot the $c$ values measured
+  for each solute with each model from lowest to highest. In general, $c$ values generated
+  by the MSDDM model are smaller than the those generated by the sFBMcut AD model 
+  because the AD model has to compensate for high $\beta$ values. Comparison 
+  of Figure~\ref{fig:c_parameters} with Figures~\ref{fig:flux_curves_ad} 
+  and~\ref{fig:flux_curves_msddm} reveals that the ranking of the $c$ parameters is
+  consistent with the ranking of solute flux. Therefore, it is reasonable to hypothesize
+  that any parameter which acts to modify the rate at which solutes move through the
+  membrane pores will affect $c$ for various physical reasons. In 
+  Figure~\ref{fig:c_influence} we demonstrate that decreased dwell times
+  (increased $\alpha_d$), increased hop lengths (increased $\sigma$), cutting off the
+  dwell time distribution at shorter times (increased $\lambda$) and increased tail 
+  weights of the hop length distribution (decreased $\alpha_h$) independently lead to
+  an increase in $c$. Figure~\ref{fig:c_influence} also suggests that $c$ is not dependent on hop
+  anti-correlation ($H$).
+
+%  We showed earlier that $\beta$ is not a
+%  function of $\sigma$ or $\alpha_d$, therefore dwell times and hop lengths must
+%  influence $c$. In fact, any parameter which acts to modify the rate at which 
+%  solutes move through the membrane pores will affect $c$. Therefore it is 
+%  sensible to hypothesize that a higher degree of anti-correlation (lower $H$)
+%  should decrease $c$ and a higher value of $\alpha_h$ should also increase $c$.
+%  In Figure~\ref{fig:c_influence}, we verify these hypotheses by holding
 
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.42\textwidth}
+  % use c_parameters2.py
   \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
+  \begin{subfigure}{0.53\textwidth}
+  \vspace{0.5em}
+  \includegraphics[width=\textwidth]{c_influence.pdf}
   \caption{}\label{fig:c_influence}
   \end{subfigure}
-  \caption{(a) The c paramters are directly related to your mom (b) }\label{fig:c}
+  \caption{(a) The $c$ parameter increases with solute flux (compare ranking with
+  Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm}). The $c$ parameters
+  of the MSDDM are smaller than the sFBMcut AD model because the AD model must
+  compensate for its strong length dependence (higher $\beta$). (b) Changes to parameters
+  which increase the rate of solute displacement result in larger values of $c$. 
+  To test the dependence of $c$ on $\alpha_d$, $\sigma$, $H$ and $\lambda$, we chose a 
+  single set of parameters, representative of solutes parameterized by the sFBMcut AD model,
+  and generated realizations of the model by varying each parameter independently about the
+  same base parameter set. Therefore, the middle bars for these four 4 parameters are 
+  generated from the same set of parameters. Decreased dwell times (increased $\alpha_d$),
+  increased hop lengths (increased $\sigma$), and a lower cut-off to the dwell time
+  distribution (increased $\lambda$) lead to increases in $c$. $c$ responds linearly
+  to increases in $\sigma$ and $\lambda$ and non-linearly to $\alpha_d$. The data 
+  suggests that the $c$ parameters do not depend on hop anti-correlation ($H$). To test 
+  $\alpha_h$, we used the set of parameters defining the MSDDM of Urea (since sFBMcut does
+  not use a L\'evy distribution) and varied the $\alpha_h$ parameter of the transitional
+  hops. As $\alpha_h$ increases, $c$ decreases since the probability of large hops decreases.
+  We expect similar dependence of $c$ on $\sigma$ and $H$ of the MSDDM.}\label{fig:c}
   \end{figure}
@@
   the data suggests that this particular LLC membrane might be most useful for 
-  selectively separating ethylene glycol from acetic acid.
-
-  Out of the solutes studied, the data suggests that this particular LLC membrane 
-  %MRS5: would is a bit strong given the number of limitations.
-  %would 
-  might
-  be most useful for selectively separating ethylene glycol from methanol and 
-  acetic acid. 
-  %It also shows reasonable selectivity of Urea over acetic acid.  
-  Ethylene glycol has the highest $c$ value and the lowest $\beta$ value. The high
-  value of $c$ itself greatly enhances its selective passage. Even more importantly,
-  the relatively large difference between its $\beta$ value and those of methanol 
-  and acetic acid give rise to a strong pore length dependence. The selectivity is
-  enhanced as the pore length increases at the cost of lower solute flux, a 
-  phenomenon ubiquitous in polymer separations membranes.~\cite{geise_water_2011}
-
-  Of course, this approach to modeling LLC membrane selectivity neglects a number of
-  factors that influence real-world aqueous membrane separations. The most glaring is 
-  that we neglected convective flux which should work to increase overall solute flux 
-  and lower selectivity (see Equation ~\ref{eqn:solute_flux}). Defects in the pore 
-  structure will have a strong influence on solute flux which may exacerbate the length 
-  dependence of flux. Even in a perfectly structured membrane, the barrier to pore
-  entry from the bulk solution will have its own influence on experimentally observed 
-  selectivities. This energetic barrier can be made even worse by foulants deposited on
-  the membrane's surface. Therefore, our predictions should be primarily used to 
-  identify the most promising types of selective separations for an H\textsubscript{II}
-  LLC membrane made from a specific monomer.
+  selectively separating ethylene glycol from acetic acid. Ethylene glycol
+  exhibits the highest flux while acetic acid has the lowest. Ethylene glycol
+  has the weakest dependence on pore length (lowest $\beta$) according to the
+  sFBMcut model, while acetic acid has the second highest dependence. This 
+  analysis certainly merits further experimental exploration.
+
+%  Out of the solutes studied, the data suggests that this particular LLC membrane 
+%  %MRS5: would is a bit strong given the number of limitations.
+%  %would 
+%  might
+%  be most useful for selectively separating ethylene glycol from methanol and 
+%  acetic acid. 
+%  %It also shows reasonable selectivity of Urea over acetic acid.  
+%  Ethylene glycol has the highest $c$ value and the lowest $\beta$ value. The high
+%  value of $c$ itself greatly enhances its selective passage. Even more importantly,
+%  the relatively large difference between its $\beta$ value and those of methanol 
+%  and acetic acid give rise to a strong pore length dependence. The selectivity is
+%  enhanced as the pore length increases at the cost of lower solute flux, a 
+%  phenomenon ubiquitous in polymer separations membranes.~\cite{geise_water_2011}
 
@@
 
-  % BJC4: Say something about pore entry and exit as an improvement to the model
-
   We have tested two different mathematical frameworks for describing solute
@@
   solute trajectories generated by MD simulations. In almost all cases, large 
-  portions of the MSDs predicted by our model fall within the 1-$\sigma$
+  portions of the MSDs predicted by our models fall close to or within the 1$\sigma$
   confidence intervals of MD. Aside from inaccuracies in parameter estimates,
-  the most significant shortcoming of all models is their ability to 
-  accurately portray the curvature of the MSD curves. The MD MSD curves tend
-  to  become linear on long timescales, but the MSD curves generated by our
-  models have persistent curvature that may cause them to under-predict
-  the MSD on very long timescales.
+  the most significant shortcoming of all of our models is their ability to 
+  accurately portray the curvature of the MSD curves. The MD MSD curves tend to 
+  become linear on long timescales, but the MSD curves generated by our models
+  have persistent curvature that causes them to under-predict the MSD on very
+  long timescales. This is a consequence of the correlation structure associated
+  with fractional motion. In the future, we could address this by 
+  implementing a truncation to the positional autocorrelation function.
 
   We demonstrated how one could used our models in order to to determine
-  macroscopic flux and selectivity.
-  %BJC5: I'll write the rest of this paragraph after I finish the MSDDM flux calculations.
+  macroscopic flux and selectivity. We showed that, when using the AD model, 
+  solute flux decreases with pore length at a rate faster than pure 
+  Brownian motion due to anti-correlation between hops. However, using the
+  MSDDM, we observed a decay in flux similar to Brownian motion. This is
+  primarily due to the inexact method that we use to correlate hops of the 
+  fractional L\'evy motion process. When we replace FLM with FBM in the 
+  MSDDM algorithm, we observe a flux decay more consistent with that predicted
+  by the AD model. Finally, we used the ratio of solute fluxes in order to
+  calculate selectivity. Due differences in hop anti-correlation, we observe
+  a length dependent selectivity. However, this length dependence mostly
+  plateaus at length scales that can be synthesized experimentally. The data
+  suggests that this particular membrane may be useful for separating
+  ethylene glycol and acetic acid.
+
+  % BJC5: I'm not sure if this paragraph belongs here. Or if it should go at end
+  % of previous section. Or just eliminate. What do you think?  
+  Of course, our approach to modeling LLC membrane selectivity neglects a number
+  of factors that influence real-world aqueous membrane separations. The most 
+  glaring is that we neglected convective flux which should work to increase 
+  overall solute flux and lower selectivity (see Equation ~\ref{eqn:solute_flux}).
+  Defects in the pore structure will have a strong influence on solute flux which
+  may exacerbate the length dependence of flux. Even in a perfectly structured 
+  membrane, the barrier to pore entry from the bulk solution will have its own 
+  influence on experimentally observed selectivities. This energetic barrier can 
+  be made even worse by foulants deposited on the membrane's surface. Therefore,
+  our predictions should be primarily used to identify the most promising types
+  of selective separations for an H\textsubscript{II} LLC membrane made from a 
+  specific monomer.
 
@@
   to solutes with long or short hop lengths and dwell times. The MSDDM is a 
-  powerful way to characterize explicit trapping mechanisms. Although its
-  predictive power is inferior to the anomalous diffusion model, it clearly
+  powerful way to characterize explicit trapping mechanisms. It clearly
   partitions a trajectory into discrete mechanisms and quantifies their
@@
   hydrogen bonding dominates ethylene glycol. If one re-designs an LLC monomer
-  to eliminate one source of trapping, 
-  %MRS4: by what mechanisms are high selectivities possible?
-  then high selectivities are possible.
+  to eliminate one source of trapping, then high selectivities are possible.
+  Overall, in tandem or separately, our models facilitate new ways of approaching
+  complex separation problems.
 
@@
 
+  %BJC5: still a work in progress
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=3.25in]{toc.pdf}
+  \end{figure}
+
 \end{document}

### 2020-01-03 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Updates to figures

@@
 
-\title{Supporting Information: Time Series Modeling of Solute Transport in an H\textsubscript{II} 
-Phase Lyotropic Liquid Crystal Membrane}
+\title{Supporting Information: Time Series Modeling of Varying Complexity Captures 
+Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   post-simulation trajectory analysis. Paths preceding script names are relative to the
-  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second columns lists the section in the main
+  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second column lists the section in the main
   text where the output or usage of the script is first described. The third column
@@
   equilibration time points.
+
+  %Note that the partition of acetic acid appears
+  %to be oscillating slowly. We do not expect the system to plateau on a
+  %reasonable time scale, so we settled for including a complete oscillation.
 
@@
 
-  \subsection{Achieving the right correlation structure}\label{section:flm_correlation}
-
-  We simulated FLM using the algorithm of Stoev and Taqqu~\cite{stoev_simulation_2004}.
-  There are no known exact methods for simulating FLM. As a consequence, passing a
-  value of $H$ and $\alpha$ to the algorithm does not necessarily result in the correct
-  correlation structure, although the marginal L\'evy stable distribution is correct. 
-  We applied a database-based empirical correction in order to use the
-  algorithm to achieve the correct marginal distribution and correlation structure.
-
-  Stoev and Taqqu note that the transition between negatively and positively correlated
-  draws occurs when $H = 1/ \alpha$. When $\alpha=2$, the marginal distribution is 
-  Gaussian and the transition occurs at $H=0.5$ as expected from FBM. We corrected 
-  the input $H$ so that the value of $H$ measured based on the output sequence equaled
-  the desired $H$. We first adjusted the value of $H$ by adding ($1 / \alpha - 0.5$),
-  effectively recentering the correlation sign transition for any value of $1 \leq \alpha \leq 2$.
-  This correction alone does a good job for input $H$ values near 0.5, but is
-  insufficient if one desires a low value of $H$. The exact correction to $H$ is 
-  not obvious so we created a database of output $H$ values tabulated as a function
-  of input $H$ and $\alpha$ values. Figure~\ref{fig:hurst_correction} demonstrates the
-  results of applying our correction. Without the correction, FLM realizations are
-  more negatively correlated. This would result in under-predicted mean squared
-  displacements when applying the model.
-
-  % /supporting_figures/demonstrate_hurst_correction.py
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{hurst_correction.pdf}
-  \caption{Correcting the Hurst parameter input to the algorithm of Stoev and Taqqu
-  results in an FLM process with a more accurate correlation structure. We generated
-  sequences with an input $H$ of 0.35. We estimated $H$ by fitting the autocorrelation
-  function. Without the correction, $H$ is underestimated, meaning realizations are 
-  more negatively correlated than they should be.}\label{fig:hurst_correction}
-  \end{figure}
-
+  % ordered this way to be consistent with mentions in the main text
   \subsection{Truncated L\'evy stable hop distributions}\label{section:truncation}
@@
 
+  \subsection{Achieving the right correlation structure}\label{section:flm_correlation}
+
+  We simulated FLM using the algorithm of Stoev and Taqqu~\cite{stoev_simulation_2004}.
+  There are no known exact methods for simulating FLM. As a consequence, passing a
+  value of $H$ and $\alpha$ to the algorithm does not necessarily result in the correct
+  correlation structure, although the marginal L\'evy stable distribution is correct. 
+  We applied a database-based empirical correction in order to use the
+  algorithm to achieve the correct marginal distribution and correlation structure.
+
+  Stoev and Taqqu note that the transition between negatively and positively correlated
+  draws occurs when $H = 1/ \alpha$. When $\alpha=2$, the marginal distribution is 
+  Gaussian and the transition occurs at $H=0.5$ as expected from FBM. We corrected 
+  the input $H$ so that the value of $H$ measured based on the output sequence equaled
+  the desired $H$. We first adjusted the value of $H$ by adding ($1 / \alpha - 0.5$),
+  effectively recentering the correlation sign transition for any value of $1 \leq \alpha \leq 2$.
+  This correction alone does a good job for input $H$ values near 0.5, but is
+  insufficient if one desires a low value of $H$. The exact correction to $H$ is 
+  not obvious so we created a database of output $H$ values tabulated as a function
+  of input $H$ and $\alpha$ values. Figure~\ref{fig:hurst_correction} demonstrates the
+  results of applying our correction. Without the correction, FLM realizations are
+  more negatively correlated. This would result in under-predicted mean squared
+  displacements when applying the model.
+
+  % /supporting_figures/demonstrate_hurst_correction.py
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{hurst_correction.pdf}
+  \caption{Correcting the Hurst parameter input to the algorithm of Stoev and Taqqu
+  results in an FLM process with a more accurate correlation structure. We generated
+  sequences with an input $H$ of 0.35. We estimated $H$ by fitting the autocorrelation
+  function. Without the correction, $H$ is underestimated, meaning realizations are 
+  more negatively correlated than they should be.}\label{fig:hurst_correction}
+  \end{figure}
+
   \newpage
@@
   $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
-  $$IC: t = 0, c = M\delta(z)$$
-  where $M$ is the total number of particles in the system. It has been shown 
+  $$IC: t = 0, c = \delta(z)$$ % M\delta(z)
+  %where $M$ is the total number of particles in the system. 
+  It has been shown 
   elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}

### 2020-01-06 Ben_Manuscripts/stochastic_transport/Draft.tex
added clarifying comment
Comments from Shirts.

@@
 %BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
-\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
-and Predicts Long Timescale Behavior in Nanoscale Pores.}
+%MRS6: I would focus first on the outputs.  Not sure about the behavior/vs. selectivity.  Probably 
+% selelctivity since it's more results oriented. ``of varying complexity'' is unneeded in the titel
+%\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
+%and Predicts Long Timescale Behavior in Nanoscale Pores.}
+\title{Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores
+with time series modeling}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   membrane, in order to predict solute mean squared displacements (MSDs) 
-  and solute flux in macroscopic length pores. With our first model, based on 
-  the anomalous diffusion theory, we show how solute dynamics can be modeled 
+  and solute flux,
+  %MRS6: added
+  and thus solute selectivity, 
+  in macroscopic length pores. 
+  %MRS6: tweak
+  %With our first model, based on the 
+  First, using
+  anomalous diffusion theory, we show how solute dynamics can be modeled 
   as a fractional diffusion process subordinate to a continuous time random 
@@
   applies 2 sets of parameters based on the solute's radial distance from the
-  closest pore center. Our second model, a generalization of Markov state models,
-  treats the configurational state of the system as a Markov process, each of
-  which has state dependent transport behavior. For each state and transition
+  closest pore center. 
+  %MRS6: tweak.
+
+  Next, we generalize Markov state models,
+  treating the configurational state of the system as a Markov process, each 
+  %MRS6: tweak
+  %of which has state dependent transport behavior. 
+  state of which has separate transport properties
+  For each state and transition
   between states, we parameterize the distribution and temporal correlation 
@@
   allow us to predict solute MSDs. We show that our models reasonably reproduce
-  the MSDs calculated from MD simulations. Finally, we demonstrate how one can
-  use our models in order to calculate flux of a given solute across a 
+  the MSDs calculated from MD simulations.
+
+  Finally, we demonstrate how one can
+  use our models 
+  %in order to calculate 
+  to estimate
+  flux of a 
+  %given 
+  solute across a 
   macroscopic-length pore and, based on those quantities, the membrane's selectivity
-  towards each solute. Overall, this work helps connect the relationship between
+  towards each solute. Overall, this work helps to connect 
+  % the relationship between
   microscopic chemically-dependent solute motions and macroscopic membrane performance.
@@
   in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
-  Two types of LLC membranes are in active development. The inverted hexagonal, 
+  Tweaks.
+  Two
+  general types of LLC membranes 
+  are 
+  being actively developed.
+  %in active development. 
+  The inverted hexagonal, 
   H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
@@
   subset of LLC monomers have been studied experimentally in membrane applications.
+  %MRS6: should these references be contracted?
   \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
@@
   of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
+  %MRS6: sentence seems out of place here? True, but does it support the thesis here?
   The H\textsubscript{II} phase is a simpler geometry to model than the Q\textsubscript{I} phase.  
@@
   with some quantitative support which already allows us to speculate about new LLC
-  monomer designs, however they would be of greater value to a wider audience if we 
+  monomer designs
+  %MRS6: breaking sentence.
+  However, they would be of greater value to a 
+  %wider audience 
+  larger set of reseachers
+  if we 
   could provide quantitative predictions of macroscopic observables such as solute 
@@
   it is prohibitively expensive and time-consuming to run simulations longer than 
-  those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
+  those performed for this work ($\sim$5 $\mu$s). 
+  %MRS:deleting.
+  %And 
+  Even with the relatively large 
   size of our system, we only simulate 24 solute trajectories per unit cell in order
@@
   Using a bottom-up modeling approach, we can parameterize single particle behavior
-  by reducing our MD simulations to observations of several key properties
+  by 
+  %MRS6:
+  extracting from 
+  %reducing
+  our MD simulations 
+  %to observations of several key 
+  properties
+  of their trajectories
   that have the greatest influence on solute dynamics and then construct an ensemble 
-  of characteristic single solute trajectories useful for making long timescale
+  of characteristic single solute trajectories 
+  with these properties
+  useful for making long timescale
   predictions with computational ease and lower uncertainties. Fortunately, there 
@@
   observations from our previous work and their inputs are parameterized using a 
-  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
+  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. 
+  %MRS6: maybe rephrase the next - 'dive' is kind of casual?  Also, it seems more like the start of the next paragraph.
+  The formulation
   of these models requires a dive into stochastically driven processes.
@@
   researchers formulate hypotheses to explain why a certain set of parameters is
-  characteristic to a specific solute. This is largely the approach we used to
+  characteristic to a specific solute. 
+  %MRS6: next sentence implies you used sFBM to uncover the mechanisms of the last paper, but that detail wasn't really there? 
+  This is largely the approach we used to
   discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
@@
   is better but to evaluate their performance independently because they both
-  have potential value dependent on one's research goals. The anomalous subdiffusion
+  have potential value dependent on 
+  %MRS:
+  %one's research
+  a give reseach study's
+  goals. The anomalous subdiffusion
   approach provides a systematic way to compare the dynamical behavior of different
@@
   anti-correlated solute hopping behavior severely reduces flux relative to 
-  uncorrelated behavior. We use the relative solute fluxes to calculate the 
+  uncorrelated behavior. We use the relative solute fluxes to 
+  %MRS6: tweak
+  %calculate 
+  estimate
+  the 
   membrane's selectivity between all pairs of solutes and demonstrate that, when 
@@
 
-  We ran all MD simulations and energy minimizations using GROMACS 2018.  %BJC4: version 2018. That's it not 2018.3 or anything. 
-  ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
-  We performed all post-simulation trajectory analysis using python scripts which 
+  We ran all MD simulations and energy minimizations using GROMACS 2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
+%BJC4: version 2018.
+That's it not 2018.3 or anything.
+  We performed all post-simulation trajectory analysis using Python scripts which 
   are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
@@
   used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
-  straight and uniform sized pores. Water present in the distal tail region is omitted 
+  straight and uniform sized pores. Water present in the 
+  %MRS6: isn't distal tail redundant? 
+  distal tail region is omitted 
   for clarity.}\label{fig:membrane_structure}
@@
 
-  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
+  Solutes in this system 
+  %MRS6: added
+  very clearly 
+  exhibit 
+  subdiffusive behavior, a type of anomalous diffusion.
   During an anomalous diffusion process, the mean squared displacement (MSD)
   does not grow linearly with time, but instead it follows a power law of the form:
+  %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
   \begin{equation} 
@@
 
+  %MRS6: next paragraph could be clearer.  Maybe motivate at the beginning why the importance of time. vs. ensemble averated. It's sprung a sort of a surprise there's a difference 
   We analyzed the time-averaged MSD of the simulated trajectories by measuring
@@
   because, compared to the ensemble average, it is a more statistically robust measure
-  of the average distance a solute travels over time. Although theoretically possible, we do
+  of the average distance a solute travels over time. 
+  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
+  Although theoretically possible, we do
   not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
@@
   One can characterize the CTRW component of an sFBM process by the parameters which describe
-  its dwell time and hop length distributions. We used the \texttt{ruptures} python
+  its dwell time and hop length distributions. We used the \texttt{ruptures} Python
   package in order to automatically identify mean shifts in solute trajectories, 
@@
   now proportional to $t^{-1 - \alpha_d}e^{-\lambda t}$.
+  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
   % of the form:
@@
   are so close to zero. Therefore, we obtained H by performing a least squares fit of 
-  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 0.5 ns time lags of the 
+  Equation~\ref{eqn:fbm_autocorrelation} to the first 
+  ten  
+  0.5 ns time lags of the 
   empirically measured autocorrelation function.
@@
   \subsubsection{Subordinated Fractional L\'evy Motion}\label{method:sflm}
-
-  If the distribution of hops is not Gaussian, we can model them with the
+  %MRS6: maybe make it clearer that this is something you will be doing in the paper 
+  Since we also want to account for the possibility that
+  %If the 
+  distribution of hops is not Gaussian, we can model them with the
   more general class of L\'evy stable distributions. For independent and identically
@@
   describes the Fourier transform of a L\'evy stable PDF is:
+  %MRS6: maybe use just $\alpha$ for the general subdiffusive case, and alpha_h here.   
   \begin{equation}
@@
   parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter. The most
-  familiar case, and 1 of 3 that can be expressed in terms of elementary functions,
+  familiar case, and one of three that can be expressed in terms of elementary functions,
   is the Gaussian PDF ($\alpha_h$ = 2, $\beta$ = 0). We assume symmetric distributions
@@
   $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
-  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
+  $T_{sim}$ varied 
+  %MRS6:
+  between solutes
+  due to differing solute equilibration times. We constructed 
   trajectories by simulating sequences of dwell times and correlated hop lengths
@@
   incorporated by re-sampling each row from a two dimensional Dirichlet distribution
-  (also called a beta distribution for the 2D case) with concentration parameters 
+  %MRS6:
+  %(also called a 
+  (which is also a 
+  beta distribution for the 2D case) with concentration parameters 
   defined by the count matrix.~\cite{bacallado_bayesian_2009}
@@
   %BJC3: not sure how to cite fbm
-  We used the python package \texttt{fbm} to generate exact simulations of FBM and our
-  own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
+  We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
+  own Python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
   \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
-  simulation algorithms for generating FLM trajectories, however, the algorithm
+  simulation algorithms for generating FLM trajectories. 
+  %MRS6: broke sentence
+  However, the algorithm
   we used sufficiently approximates draws from the marginal distribution and 
@@
   validation of the approach).
-
+  %MRS6: suggest in the supporting information describe what measure was used to determine that the algorithm sufficiently and reasonably approxmiates.
 %  When simulating 5 $\mu s$ FLM trajectories, we limited the maximum hop length to
@@
   the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
+  %MRS6: maybe skip this next sentence since you don't actually use them?
   Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
@@
   assume that there are no significant kinetic effects resulting from solute 
-  conformational changes or pore size fluctuations, an assumption that may be 
-  relaxed in future work. We use the same radial cut-off (0.75 nm) as in the 
+  conformational changes or pore size fluctuations. 
+  %MRS6:
+  %Eh, Don't need to talk about future work. 
+  %an assumption that may be relaxed in future work.
+
+  We use the same radial cut-off (0.75 nm) as in the 
   anomalous diffusion model to differentiate the pore and tail region.  We define 
@@
   30$\degree$. We define a sodium ion to be associated with an atom if they are 
-  within 2.5 \AA~of each other.~\cite{coscia_chemically_2019}
+  within 2.5 \AA~of each other, 
+  %MRS6:
+  as determined in our previous work~\cite{coscia_chemically_2019}
 
@@
 
-  \subsection{Solute Flux}\label{method:mfpt}
+  %\subsection{Solute Flux}\label{method:mfpt}
+  %MRS6: tweak to make more active
+  \subsection{Estimating Solute Flux}\label{method:mfpt}
 
@@
   to construct a distribution of first passage times across a membrane pore of length $L$.
-  For computational reasons dependent on the model used, we simulated 1000-10000 trajectory
+  For computational reasons dependent on the model used, we simulated 1,000-10,000 trajectory
   realizations, released at the pore entrance ($z=0$). In the case of 
@@
 
+%MRS6: maybe more subsections in results so people can get a sense of where the flow is going at a glance?
   \section{Results and Discussion}
@@
   The evidence suggests that solutes in this system can be well-modeled by subordinated
-  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use Urea to
+  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use urea to
   support this claim. Analogous figures for all other solutes are presented in the Supporting
@@
   %BJC4: added
+  %MRS6: I'm wondering if the other plots should be in the main text.  They are part of the core of the paper, showing that the modeling is reasonable. 
   \end{figure}
@@
   \includegraphics[width=0.5\textwidth]{ad_realizations_1mode.pdf}
-  \caption{Simulations of 1 mode AD model trajectories for Urea display qualitatively
+  \caption{Simulations of 1 mode AD model trajectories for urea display qualitatively
   similar hopping and trapping behavior to that shown in Figure~\ref{fig:solute_trajectories}. 
@@
   %Analogous plots are shown for other solutes
+  %MRS6: I don't think the comparison between the cut and no cut are that interesting for the main text.  Move to supporting?
+  %MRS6: comparisons between modeled and actual trajectories side by side would be more interesting. 
   %BJC5: todo: add plots to SI. Show I add a 2 mode model plot?
@@
 
+  %MRS6: you don't say what is in the paragraphs.
   \end{tabular}
@@
   \end{subfigure} 
+  %MRS6: I'm not sure I see red in urea.  Is the uncertainty that low?
   \caption{In most cases, when using power laws with exponential cut-offs 
@@
   solute data. The models which use pure power laws systematically under-predict
-  the MD MSD curves. Improper curvature of the MSD curves cause the magnitude of
+  the MD MSD curves. 
+  %MRS6: be more specific when you say ``improper''. What is improper?
+Improper curvature of the MSD curves cause the magnitude of
   the urea's predicted MSDs to be under-predicted at long timescales and those
   of acetic acid to be under-predicted at short timescales.}\label{fig:train_test}
+  %MRS6: I'm not sure it makes sense to show the ``without cutoff'' lines here.  Maybe supporting?  
+  %MRS6: I'm just not sure it really pushes the paper forward to show more data that something you've shown
+  %MRS6: isn't likely to work earlier still isn't working. 
   \end{figure}
@@
   The under-estimate of Urea's MSD at long timescales is due to long timescale
-  positional anti-correlation which may not be present in the real system. The 
+  positional anti-correlation which may not be present in the 
+  %MRS6: real?
+  %real 
+  molecularly detailed simulations of the 
+  system. The 
+  %MRS6: I'm not following whether or not there should be positional anti-correlation.  I was thinking there should be,
+  %but perhaps I'm misunderstanding something here? 
   persistent curvature of the predicted MSD curves is a direct consequence of 
@@
   but also lower the predicted MSD meaning we are either underestimating the width of
-  the hop length distribution, favoring longer dwell times or both.
+  the hop length distribution, favoring longer dwell times, or both.
 
@@
   full equilibrated portion of the solute trajectories, doubling the data.
+
+%MRS6: My instinct is to only show the graphs of the full model, with validation graphs shown in the supporting.
+We can talk about this.
+We do what the focus to be on what we can learn physically.
+The discussion gets pretty repetitive.
+
+%MRS6: be a bit clearer about how the MD MSD error bounds are calculated.  That becomes important for determining how accurate the modeling is. .
 
@@
   \caption{
+  %MRS6: shouldnt the values be positive below the axis as well (if that can be done) I guess they are for b, but not for A.
   The two mode model parameterizes solute behavior in the pore and tails separately.
@@
   center, otherwise they are in the tails. (a) Generally, movement is much more restricted
-  in the tail region shown by lower $\sigma$ values for the Normal and L\'evy stable 
+  in the tail region shown by lower $\sigma$ 
+  %MRS6: define sigma to remind people what it is
+  values for the normal and L\'evy stable 
   distributions. Values of $\alpha$ are significantly lower for urea and acetic acid meaning 
@@
   to differences in their curvature at long time lags. The shape and magnitude of the curves appears accurate 
-  at short time lags, however, the curves tend to undershoot the MD MSD mean
+  at short time lags.  
+  %MRS6: which curves?
+  However, the curves tend to undershoot the MD MSD mean
   as the time lag increases. As discussed in the previous section, long time
@@
 
+  %MRS6: is it more or less physical that it has this behavior? 
   The 2 mode models shows considerably less curvature at large time lags than
@@
   limit of 0.5, indicate a lower degree of negative correlation between hops. All 
-  of which contribute to an overall increase in the MSD.
+  of 
+  these model properties
+  %which 
+  contribute to 
+  %MRS6: increase in the MSD compared to what, be specific?
+  an overall increase in the MSD.
 
@@
   the pore region due to its two hydrophilic hydroxyl groups. Meanwhile methanol 
-  spends 91 \% of its time in the tails likely due to its small size.  
-  The value of $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
+  spends 91\% of its time in the tails likely due to its small size.  
+  The value of $\alpha_h$ for urea and acetic acid in the tails is 1.50, meaning its hop distribution
   is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
@@
   states, defined in Table~\ref{table:states}, with state-dependent positional
-  fluctuations, which we call the MSDDM.
+  fluctuations, which we 
+  %MRS6:
+  refer to as
+  %call 
+  the MSDDM.
+  %MRS6: maybe give full name before if you are essentially defining it.
 
@@
   into a single distribution and measured the correlation of the series of all 
-  transitions. We lose information about individual types of transitions, however, 
+  transitions. 
+  %MRS6: how much of this is described earlier in methods?
+  We lose information about individual types of transitions, however, 
   we believe this is unavoidable without at least an order of magnitude of additional data.
@@
 
+%MRS6: even if the MSD is well predicted, if the trajectories look different, can it really be a useful model?
+I.e.
+is one getting the right answer for the wrong reasons?
+What does it mean if MSD's are good, but the dwell times are not great?
   Qualitatively, realizations of the MSDDM are not consistent with MD solute
@@
   \includegraphics[width=0.5\textwidth]{msddm_realizations.pdf}
+  %MRS6: see above - right for wrong reasons?
   \caption{Realizations of the MSDDM for each solute do not reproduce the hopping
@@
   The predicted MSD of acetic acid is severely over-estimated most likely due
-  to poor parameterization. As stated earlier, most of a solute's motion is 
+  to poor parameterization. 
+  %MRS6: poor parameterization is vague.  Of which features?
+As stated earlier, most of a solute's motion is 
   due to displacements during state transitions. Acetic acid has a transitional
@@
 
+  %MRS6: to what extent can be 'cut' models be the ones used, and the untruncated ones thrown out early in the paper to simplify the presentation. 
   We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
@@
   \end{subfigure}  
-  \caption{(a) The distributions of passage times generated from the sFBMcut model
+  %MRS6: make clear the dots are experiment. 
+  \caption{(a) The distributions of first passage times generated from the sFBMcut model
   fit well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
@@
   flux, with minimal change to the mean flux values, using as few as 100 trajectory
-  realizations. To be sure, we recommend simulating at least 1000 realizations. 
+  realizations. 
+  %To be sure, 
+  For better precision, we recommend simulating at least 1000 realizations. 
   Since the computational cost of the MSDDM is greater than the AD model, we generated
@@
   %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
+  %MRS6: should try to lead with what the overall results/conclusions are.
+What does it mean that parameters are larger or smaller?
+What should the reader take from the discussion?
+Should it be in supportinig?
   \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
@@
 
+  %MRS6: can this be made a physical thesis instead of a mathematical one?
   The values of $c$ are directly related to the magnitude of solute flux and, where
@@
   \end{subfigure}
+  %BJC5: waiting on simulations for alpha_h
   \caption{(a) The $c$ parameter increases with solute flux (compare ranking with
@@
   offer important mechanistic insight on the molecular details of transport.
-  Subordinated fractional Brownian and L\'evy motion have a nice theoretical 
+  Subordinated fractional Brownian and L\'evy motion have a 
+  %nice 
+  strong theoretical 
   foundation in the anomalous diffusion literature. Our single mode model
@@
 
+  %MRS6: right answer, wrong reason for MSD match issue?
   All of the models we tested have moderate success reproducing the MSDs of
@@
 
+  %MRS6: look over and make bibliography consistent (i.e. no months, consistent journal abbreviations)
   \bibliographystyle{ieeetr}
@@
   %BJC5: still a work in progress
+  %MRS6: seems pretty reasonable as a concept.
+If you can make the three figure labels the same color (doesn't have to be black or white) and same font, might be nice.
+Maybe make arrows more like circle arcs, and change the color from black so it stands out more?
+The time series model figure is a bit busy.
+Can it be reduced from 4 subfigures?
+May not be necessary, but one thing to think about.
   \begin{figure}[!htb]

### 2020-01-06 Ben_Manuscripts/stochastic_transport/Draft.tex
Incorporating MRS edits

@@
 %and Predicts Long Timescale Behavior in Nanoscale Pores.}
+% BJC6: The only issue with selectivity is that I don't think it would include a timescale.
 \title{Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores
@@
   \begin{abstract}
+
   Mathematically modeling complex transport phenomena at the molecular level 
@@
   membrane, in order to predict solute mean squared displacements (MSDs) 
-  and solute flux,
-  %MRS6: added
-  and thus solute selectivity, 
-  in macroscopic length pores. 
-  %MRS6: tweak
-  %With our first model, based on the 
-  First, using
-  anomalous diffusion theory, we show how solute dynamics can be modeled 
-  as a fractional diffusion process subordinate to a continuous time random 
-  walk. From the MD simulations, we parameterize the distribution of 
+  and solute flux, and thus solute selectivity, in macroscopic length pores. 
+  First, using anomalous diffusion theory, we show how solute dynamics can be
+  modeled as a fractional diffusion process subordinate to a continuous time 
+  random walk. From the MD simulations, we parameterize the distribution of 
   dwell times, hop lengths between dwells and correlation between hops. We 
@@
   applies 2 sets of parameters based on the solute's radial distance from the
-  closest pore center. 
-  %MRS6: tweak.
-
-  Next, we generalize Markov state models,
-  treating the configurational state of the system as a Markov process, each 
-  %MRS6: tweak
-  %of which has state dependent transport behavior. 
-  state of which has separate transport properties
-  For each state and transition
+  closest pore center. Next, we generalize Markov state models, treating the
+  configurational state of the system as a Markov process, each
+  of which has separate transport properties. For each state and transition
   between states, we parameterize the distribution and temporal correlation 
@@
   allow us to predict solute MSDs. We show that our models reasonably reproduce
-  the MSDs calculated from MD simulations.
-
-  Finally, we demonstrate how one can
-  use our models 
-  %in order to calculate 
-  to estimate
-  flux of a 
-  %given 
-  solute across a 
-  macroscopic-length pore and, based on those quantities, the membrane's selectivity
-  towards each solute. Overall, this work helps to connect 
-  % the relationship between
-  microscopic chemically-dependent solute motions and macroscopic membrane performance.
+  the MSDs calculated from MD simulations. Finally, we demonstrate how one can
+  use our models to estimate flux of a solute across a macroscopic-length pore
+  and, based on those quantities, the membrane's selectivity towards each solute.
+  Overall, this work helps to connect microscopic chemically-dependent solute 
+  motions and macroscopic membrane performance.
 
@@
   and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
-  %BJC5: made more general. 
-  there is a strong interest in creating breathable fabrics % barriers 
-  % to chemical warfare agents
-  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
+  there is a strong interest in creating breathable fabrics which selectively allow 
+  passage of water vapor.~\cite{mondloch_destruction_2015}
 %  The pace at which we achieve these or any other selective separation goals will be 
@@
   cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
-  They may provide a promising alternative to 
-  % have the potential to disrupt
-  conventional membrane separation techniques by being selective based not only on solute
-  size and charge, but on solute chemical functionality as well.~\cite{dischinger_application_2017}
-  One can tune the functionality of LLC monomers
-  in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
-  Tweaks.
-  Two
-  general types of LLC membranes 
-  are 
-  being actively developed.
-  %in active development. 
-  The inverted hexagonal, 
+  They may provide a promising alternative to conventional membrane separation techniques
+  by being selective based not only on solute size and charge, but on solute chemical 
+  functionality as well.~\cite{dischinger_application_2017} One can tune the functionality
+  of LLC monomers in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
+  Two general types of LLC membranes are being actively developed. The inverted hexagonal, 
   H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
@@
   %MRS6: should these references be contracted?
+  %BJC6: probably, will see if that gets fixed by journal latex template
   \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
@@
   %MRS6: sentence seems out of place here? True, but does it support the thesis here?
-  The H\textsubscript{II} phase is a simpler geometry to model than the Q\textsubscript{I} phase.  
+  %BJC6: I said above how the QI phase is easier to synthesize, so I felt it necessary to 
+  % quickly justify why we studied the HII phase. Reworded to make that clearer. I'm also open to
+  % eliminating the sentence.
+  We chose to study the H\textsubscript{II} phase because it is a simpler geometry to model than 
+  the Q\textsubscript{I} phase.  
   In general, we observed subdiffusive transport behavior characterized by intermittent hops 
@@
   with some quantitative support which already allows us to speculate about new LLC
-  monomer designs
-  %MRS6: breaking sentence.
-  However, they would be of greater value to a 
-  %wider audience 
-  larger set of reseachers
-  if we 
-  could provide quantitative predictions of macroscopic observables such as solute 
-  flux and selectivity. Due to the size of the types of systems we are studying (at least 62,000 atoms)
-  it is prohibitively expensive and time-consuming to run simulations longer than 
-  those performed for this work ($\sim$5 $\mu$s). 
-  %MRS:deleting.
-  %And 
-  Even with the relatively large 
-  size of our system, we only simulate 24 solute trajectories per unit cell in order
+  monomer designs. However, they would be of greater value to a larger set of 
+  researchers if we could provide quantitative predictions of macroscopic observables
+  such as solute flux and selectivity. Due to the size of the types of systems we are 
+  studying (at least 62,000 atoms) it is prohibitively expensive and time-consuming to
+  run simulations longer than those performed for this work ($\sim$5 $\mu$s). 
+  Even with the relatively large size of our system, we only simulate 24 solute trajectories per unit cell in order
   to minimize solute-solute interactions. This results in relatively high uncertainties
@@
   Using a bottom-up modeling approach, we can parameterize single particle behavior
-  by 
-  %MRS6:
-  extracting from 
-  %reducing
-  our MD simulations 
-  %to observations of several key 
-  properties
-  of their trajectories
-  that have the greatest influence on solute dynamics and then construct an ensemble 
-  of characteristic single solute trajectories 
-  with these properties
-  useful for making long timescale
-  predictions with computational ease and lower uncertainties. Fortunately, there 
-  is an abundance of information encoded in the complex solute trajectories. Into a
+  by extracting their trajectories from MD simulations and studying the properties that
+  have the greatest influence on solute dynamics. With this information, we can learn
+  how to construct an ensemble of characteristic single solute trajectories with these
+  properties which would be useful for making long timescale predictions with computational
+  ease and lower uncertainties. Fortunately, there is an abundance of information encoded
+  in the complex solute trajectories. Into a
   model, we can incorporate fluctuations and time-dependent correlations in solute
@@
   %MRS6: maybe rephrase the next - 'dive' is kind of casual?  Also, it seems more like the start of the next paragraph.
-  The formulation
-  of these models requires a dive into stochastically driven processes.
+  %BJC6: I just got rid of the sentence. It doesn't really add anything
+%  The formulation
+%  of these models requires a dive into stochastically driven processes.
 
@@
   researchers formulate hypotheses to explain why a certain set of parameters is
-  characteristic to a specific solute. 
-  %MRS6: next sentence implies you used sFBM to uncover the mechanisms of the last paper, but that detail wasn't really there? 
-  This is largely the approach we used to
-  discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
-  Once one has knowledge of the primary mechanisms leading to anomalous diffusion
-  behavior, one may gain additional insight by formulating a state-based model.
+  characteristic to a specific solute. Once one has knowledge of the primary 
+  mechanisms leading to anomalous diffusion behavior, one may gain additional
+  insight by formulating a state-based model.
 
@@
   is better but to evaluate their performance independently because they both
-  have potential value dependent on 
-  %MRS:
-  %one's research
-  a give reseach study's
-  goals. The anomalous subdiffusion
+  have potential value dependent on a given research study's goals. The anomalous subdiffusion
   approach provides a systematic way to compare the dynamical behavior of different
@@
   anti-correlated solute hopping behavior severely reduces flux relative to 
-  uncorrelated behavior. We use the relative solute fluxes to 
-  %MRS6: tweak
-  %calculate 
-  estimate
-  the 
+  uncorrelated behavior. We use the relative solute fluxes to estimate the 
   membrane's selectivity between all pairs of solutes and demonstrate that, when 
@@
   used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
-  straight and uniform sized pores. Water present in the 
-  %MRS6: isn't distal tail redundant? 
-  distal tail region is omitted 
+  straight and uniform sized pores. Water present in the tail region is omitted 
   for clarity.}\label{fig:membrane_structure}
@@
 
-  Solutes in this system 
-  %MRS6: added
-  very clearly 
-  exhibit 
-  subdiffusive behavior, a type of anomalous diffusion.
-  During an anomalous diffusion process, the mean squared displacement (MSD)
-  does not grow linearly with time, but instead it follows a power law of the form:
+  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
+  anomalous diffusion. During an anomalous diffusion process, the mean squared 
+  displacement (MSD) does not grow linearly with time, but instead it follows 
+  a power law of the form:
   %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
@@
   %MRS6: next paragraph could be clearer.  Maybe motivate at the beginning why the importance of time. vs. ensemble averated. It's sprung a sort of a surprise there's a difference 
-  We analyzed the time-averaged MSD of the simulated trajectories by measuring
-  all possible displacements over time lag $\tau$:
+  %BJC6: reorganized a little and broke into paragraphs meant to convey separate ideas.
+
+  One can measure MSD in two ways. The time-averaged MSD measures all observed
+  displacements over time lag $\tau$: 
   \begin{equation}
@@
   \end{equation}
-  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
-  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
-  MSD is given by:
+  where T is the length of the trajectory. The ensemble averaged MSD measures
+  displacements with respect to a particle's initial position:
   \begin{equation}
@@
   \end{equation}
-  In a pure CTRW, for example, the power law distribution of trapping times leads to
-  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
-  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
-  law trapping behavior, the time between hops diverges so there is no characteristic
-  measurement time scale of solute motion. In fact, as measurement time increases, the 
-  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
-  with trapping times on the order of the measurement time get incorporated into the 
-  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
-  because, compared to the ensemble average, it is a more statistically robust measure
-  of the average distance a solute travels over time. 
-  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
-  Although theoretically possible, we do
-  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
-  with higher precision using the dwell time distributions as described below.
+  Fits to the \textit{ensemble} averaged MSD will always reproduce the form of 
+  Equation~\ref{eqn:msd_form}.
+
+  The time averaged and ensemble averaged MSDs will give identical results 
+  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
+  law distribution of trapping times leads to weak ergodicity breaking.
+  In this case, the time-averaged MSD is linear while the ensemble averaged
+  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With
+  power law trapping behavior, the time between hops diverges so there is no 
+  characteristic measurement time scale of solute motion. In fact, as measurement 
+  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
+  aging, because trajectories with trapping times on the order of the measurement 
+  time get incorporated into the calculation.~\cite{bel_weak_2005}
+
+  We chose to analyze just the time-averaged MSD because, compared to the ensemble
+  average, it is a more statistically robust measure of the average distance a 
+  solute travels over time. 
+  % MRS6: does it correspond properly to the physical situation of entry into the 
+  % pore of new particles at each unit time?
+  % BJC6: no, but neither does ensemble
+  Although theoretically possible, we do not use the ensemble averaged MSD to 
+  calculate $\alpha_d$ because we can extract the same parameter with higher 
+  precision using the dwell time distributions as described below.
+
+%  Only the \textit{ensemble} averaged MSD will reproduce the form of 
+%  Equation~\ref{eqn:msd_form} in all cases.
+%  
+%  We analyzed the time-averaged MSD of the simulated trajectories by measuring
+%  all possible displacements over time lag $\tau$:
+%  \begin{equation}
+%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
+%  \end{equation}
+%  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
+%  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
+%  MSD is given by:
+%  \begin{equation}
+%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
+%  \label{eqn:ensemble_msd}
+%  \end{equation} 
+%  In a pure CTRW, for example, the power law distribution of trapping times leads to
+%  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
+%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
+%  law trapping behavior, the time between hops diverges so there is no characteristic
+%  measurement time scale of solute motion. In fact, as measurement time increases, the 
+%  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
+%  with trapping times on the order of the measurement time get incorporated into the 
+%  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
+%  because, compared to the ensemble average, it is a more statistically robust measure
+%  of the average distance a solute travels over time. 
+%  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
+%  Although theoretically possible, we do
+%  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
+%  with higher precision using the dwell time distributions as described below.
 
@@
   \subsubsection{Subordinated Fractional L\'evy Motion}\label{method:sflm}
-  %MRS6: maybe make it clearer that this is something you will be doing in the paper 
-  Since we also want to account for the possibility that
-  %If the 
-  distribution of hops is not Gaussian, we can model them with the
-  more general class of L\'evy stable distributions. For independent and identically
-  distributed random variables, the generalized central limit theorem assures 
-  convergence of the associated probability distribution function (PDF) to a 
-  L\'evy stable PDF. \cite{klages_anomalous_2008} The characteristic equation which 
-  describes the Fourier transform of a L\'evy stable PDF is:
+
+  Since we also want to account for the possibility that distribution of hops is 
+  not Gaussian, we can model them with the more general class of L\'evy stable 
+  distributions. For independent and identically distributed random variables, 
+  the generalized central limit theorem assures convergence of the associated 
+  probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
+  The characteristic equation which describes the Fourier transform of a L\'evy stable PDF is:
   %MRS6: maybe use just $\alpha$ for the general subdiffusive case, and alpha_h here.   
@@
   set of parameters fit to solute trajectories.
-%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
-%  fit to solute trajectories.
   Our second, two mode model assigns a set of parameters to each of 2 modes based
@@
   $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
-  $T_{sim}$ varied 
-  %MRS6:
-  between solutes
-  due to differing solute equilibration times. We constructed 
+  $T_{sim}$ varied between solutes due to differing solute equilibration times. We constructed 
   trajectories by simulating sequences of dwell times and correlated hop lengths
@@
   incorporated by re-sampling each row from a two dimensional Dirichlet distribution
-  %MRS6:
-  %(also called a 
-  (which is also a 
-  beta distribution for the 2D case) with concentration parameters 
+  (which is also a beta distribution for the 2D case) with concentration parameters 
   defined by the count matrix.~\cite{bacallado_bayesian_2009}
@@
   \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
-  simulation algorithms for generating FLM trajectories. 
-  %MRS6: broke sentence
-  However, the algorithm
+  simulation algorithms for generating FLM trajectories. However, the algorithm
   we used sufficiently approximates draws from the marginal distribution and 
@@
   %MRS6: suggest in the supporting information describe what measure was used to determine that the algorithm sufficiently and reasonably approxmiates.
+
 %  When simulating 5 $\mu s$ FLM trajectories, we limited the maximum hop length to
@@
   %MRS6: maybe skip this next sentence since you don't actually use them?
-  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
-  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
-  dimensional reduction which are often necessary to identify representative states.
+%  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
+%  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
+%  dimensional reduction which are often necessary to identify representative states.
 
@@
   assume that there are no significant kinetic effects resulting from solute 
-  conformational changes or pore size fluctuations. 
-  %MRS6:
-  %Eh, Don't need to talk about future work. 
-  %an assumption that may be relaxed in future work.
-
-  We use the same radial cut-off (0.75 nm) as in the 
-  anomalous diffusion model to differentiate the pore and tail region.  We define 
+  conformational changes or pore size fluctuations. We use the same radial cut-off
+  (0.75 nm) as in the AD model to differentiate the pore and tail region.  We define 
   a hydrogen bond to exist if the distance between donor, D, and acceptor, A, 
@@
   30$\degree$. We define a sodium ion to be associated with an atom if they are 
-  within 2.5 \AA~of each other, 
-  %MRS6:
-  as determined in our previous work~\cite{coscia_chemically_2019}
+  within 2.5 \AA~of each other, as determined in our previous work~\cite{coscia_chemically_2019}
 
@@
   state-dependent dynamics allows us to simulate solute trajectories.
-  %BJC5: I said below already, but I still think it belongs
+  %BJC5: I said the following earlier , but I still think it belongs
   Hence why we refer to them as Markov State-Dependent Dynamical Models (MSDDMs).
@@
 
-  %\subsection{Solute Flux}\label{method:mfpt}
-  %MRS6: tweak to make more active
   \subsection{Estimating Solute Flux}\label{method:mfpt}
@@
   %MRS6: I'm not sure I see red in urea.  Is the uncertainty that low?
+  %BJC6: I think red and orange are directly on top of each other with same error bars
   \caption{In most cases, when using power laws with exponential cut-offs 
@@
   The under-estimate of Urea's MSD at long timescales is due to long timescale
-  positional anti-correlation which may not be present in the 
-  %MRS6: real?
-  %real 
-  molecularly detailed simulations of the 
-  system. The 
+  positional anti-correlation which may not be present in the molecularly 
+  detailed simulations of the system. The 
   %MRS6: I'm not following whether or not there should be positional anti-correlation.  I was thinking there should be,
@@
   %MRS6: shouldnt the values be positive below the axis as well (if that can be done) I guess they are for b, but not for A.
+  %BJC6: yes, oversight, thanks.
   The two mode model parameterizes solute behavior in the pore and tails separately.
@@
   center, otherwise they are in the tails. (a) Generally, movement is much more restricted
-  in the tail region shown by lower $\sigma$ 
-  %MRS6: define sigma to remind people what it is
-  values for the normal and L\'evy stable 
+  in the tail region shown by lower $\sigma$ values (smaller hops) for the normal and L\'evy stable 
   distributions. Values of $\alpha$ are significantly lower for urea and acetic acid meaning 
@@
   The deviation between the 1 mode MSD predictions and MD are primarily due
-  to differences in their curvature at long time lags. The shape and magnitude of the curves appears accurate 
-  at short time lags.  
-  %MRS6: which curves?
-  However, the curves tend to undershoot the MD MSD mean
-  as the time lag increases. As discussed in the previous section, long time
+  to differences in their curvature at long time lags. The shape and magnitude of 
+  the predicted curves appears accurate relative to MD at short time lags.  
+  However, they to undershoot the MD MSD mean as the time lag increases. As 
+  discussed in the previous section, long time
   positional anti-correlation may not exist in the MD system which results 
@@
   behavior that help explain the difference between the MSDs of different solutes. 
+  %BJC6: need to double check this after alpha_h c parameter simulations are re-done
   Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
@@
   earlier preventing extremely long dwell times. Values of $H$ closer to the Brownian
-  limit of 0.5, indicate a lower degree of negative correlation between hops. All 
-  of 
-  these model properties
-  %which 
-  contribute to 
+  limit of 0.5 indicate a lower degree of negative correlation between hops. All 
+  of these model parameters contribute to 
   %MRS6: increase in the MSD compared to what, be specific?
-  an overall increase in the MSD.
+  %BJC6: made more specific
+  an overall increase in the predicted MSD and can be correlated to physical behavior 
+  that explains differences in the MD MSDs.
 
@@
   states, defined in Table~\ref{table:states}, with state-dependent positional
-  fluctuations, which we 
-  %MRS6:
-  refer to as
-  %call 
-  the MSDDM.
-  %MRS6: maybe give full name before if you are essentially defining it.
+  fluctuations, which we refer to as the Markov state-dependent dynamical model (MSDDM).
 
@@
 
+  % BJC6: cut down the following paragraph by eliminating things that are in the methods. 
+%  There are not enough 
+%  consecutive observations of each type of transition with which to study their 
+%  individual correlation structures so we grouped all transition distributions
+%  into a single distribution and measured the correlation of the series of all 
+%  transitions. 
+%  %MRS6: how much of this is described earlier in methods?
+%  We lose information about individual types of transitions, however, 
+%  we believe this is unavoidable without at least an order of magnitude of additional data.
+%  In theory, one could parameterize separate transition distributions for those
+%  which occur in the tails versus in the pores, however this would lead to a broken 
+%  correlation structure similar to that seen in the 2 mode AD model.
+
   To create an MSDDM for each solute, we determined the state sequence associated
   with each solute trajectory and then generated emission distributions of fluctuations
-  within each state as well as transitions between states. There are not enough 
-  consecutive observations of each type of transition with which to study their 
-  individual correlation structures so we grouped all transition distributions
-  into a single distribution and measured the correlation of the series of all 
-  transitions. 
-  %MRS6: how much of this is described earlier in methods?
-  We lose information about individual types of transitions, however, 
-  we believe this is unavoidable without at least an order of magnitude of additional data.
-  In theory, one could parameterize separate transition distributions for those
-  which occur in the tails versus in the pores, however this would lead to a broken 
-  correlation structure similar to that seen in the 2 mode AD model.
+  within each state as well as transitions between states. In theory, one could 
+  parameterize separate transition distributions for those which occur in the tails 
+  versus in the pores, however this would lead to a broken correlation structure 
+  similar to that seen in the 2 mode AD model.
 
@@
   (increased $\alpha_d$), increased hop lengths (increased $\sigma$), cutting off the
-  dwell time distribution at shorter times (increased $\lambda$) and increased tail 
-  weights of the hop length distribution (decreased $\alpha_h$) independently lead to
+  dwell time distribution at shorter times (increased $\lambda$) and decreased tail 
+  weights of the hop length distribution (increased $\alpha_h$) independently lead to
   an increase in $c$. Figure~\ref{fig:c_influence} also suggests that $c$ is not dependent on hop
@@
   not use a L\'evy distribution) and varied the $\alpha_h$ parameter of the transitional
-  hops. As $\alpha_h$ increases, $c$ decreases since the probability of large hops decreases.
+  hops. As $\alpha_h$ increases, $c$ increases slightly since the density of the L\'evy
+  stable PDF is shifted away from rare hops and broadened at its center.
   We expect similar dependence of $c$ on $\sigma$ and $H$ of the MSDDM.}\label{fig:c}

### 2020-01-08 Ben_Manuscripts/stochastic_transport/Draft.tex
Consolidating

@@
-\documentclass{article}
+\documentclass[12pt]{article}
 
@@
   \begin{equation} 
-  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
+  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
   \label{eqn:msd_form}
   \end{equation} 
-  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
+  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
   diffusion coefficient. We only calculate MSD with respect to the solutes' center of
-  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
-  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
+  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha < 1$
+  indicates a subdiffusive process, while values of $\alpha = 1$ and $\alpha > 1$ 
   are characteristic of Brownian and superdiffusive motion respectively.
@@
   Although theoretically possible, we do not use the ensemble averaged MSD to 
-  calculate $\alpha_d$ because we can extract the same parameter with higher 
+  calculate $\alpha$ because we can extract the same parameter with higher 
   precision using the dwell time distributions as described below.
@@
 %  Although theoretically possible, we do
-%  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
+%  not use the MSD to calculate $\alpha$ because we can extract the same parameter 
 %  with higher precision using the dwell time distributions as described below.
@@
   of dwell times is expected to fit a power law distribution 
-  proportional to $t^{-1-\alpha_d}$.~\cite{meroz_toolbox_2015}
+  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
   Because we are limited to taking measurements at discrete intervals dictated by the output 
   frequency of our simulation trajectories, we fit the empirical dwell times
-  to a discrete power law distribution whose maximum likelihood $\alpha_d$ 
+  to a discrete power law distribution whose maximum likelihood $\alpha$ 
   parameter we calculated by maximizing the likelihood function: 
@@
   \end{equation}
-  where $\beta = 1 + \alpha_d$, $t_i$ are collected dwell time data points,
+  where $\beta = 1 + \alpha$, $t_i$ are collected dwell time data points,
   $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
@@
   an exponential cut-off to the power law so the dwell time distribution is 
-  now proportional to $t^{-1 - \alpha_d}e^{-\lambda t}$.
+  now proportional to $t^{-1 - \alpha}e^{-\lambda t}$.
   %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
@@
 %  \end{equation}
-  We determine MLEs of $\alpha_d$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
+  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
   \begin{equation}
-    \mathcal{L}(\alpha_d, \lambda) = n(1 - \alpha_d)\ln\lambda - n\ln\Gamma(1 - \alpha_d, t_{min}\lambda) - \alpha_d\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
+    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
   \label{eqn:powerlaw_cutoff_likelihood}
@@
   in the L\'evy stable disributions. High values of $\sigma$ and lower values of $\alpha_h$
-  result in larger hops. (b) We parameterized a pure power law, $P(\alpha_d)$, and a 
-  truncated power law, $P_T(\alpha_d, \lambda)$, distribution to describe solute dwell
-  times. Lower values of $\alpha_d$ lead to heavier power law tails and higher values of 
+  result in larger hops. (b) We parameterized a pure power law, $P(\alpha)$, and a 
+  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe solute dwell
+  times. Lower values of $\alpha$ lead to heavier power law tails and higher values of 
   $\lambda$ truncate the distibution at lower dwell times. (c) Finally, we parameterized the
@@
   there is a larger probability that they will take large hops. (b) Dwell times are longer in 
-  the tails. Lower values of $\alpha_d$ correspond to power laws with heavier tails and 
+  the tails. Lower values of $\alpha$ correspond to power laws with heavier tails and 
   thus higher probabilities of long dwell times. There is no easily discernable trend in
@@
   hop length magnitudes by increasing the hop length distribution's width and tail 
-  density respectively. Higher values of $\alpha_d$ indicate a lower probability of 
+  density respectively. Higher values of $\alpha$ indicate a lower probability of 
   long dwell times. Higher values of $\lambda$ truncate the power law distribution 
@@
   with tails are frequent. Urea has the third highest MSD which is primarily a consequence of
-  more frequent and longer dwell times, indicated by lower values of $\alpha_d$ and 
+  more frequent and longer dwell times, indicated by lower values of $\alpha$ and 
   $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
@@
   to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
-  by an $\alpha_d$ value significantly lower than other solutes, but an intermediate 
+  by an $\alpha$ value significantly lower than other solutes, but an intermediate 
   $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
@@
   while they are in the tail region where long dwell times are more probable
-  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Each solute spends 
+  (smaller $\alpha$) and hops are smaller (smaller $\sigma$). Each solute spends 
   a different amount of time in the tails (see Figure~\ref{fig:AD_mode_occupation}). 
@@
 %  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
-%  of $\alpha_d$ for pure and truncated power law fits to the dwell time distributions of 
-%  urea, ethylene glycol and methanol are similar. The value of $\alpha_d$ for acetic
+%  of $\alpha$ for pure and truncated power law fits to the dwell time distributions of 
+%  urea, ethylene glycol and methanol are similar. The value of $\alpha$ for acetic
 %  acid is significantly lower than the rest of the solutes meaning it stays trapped 
@@
 %  is not surprising considering their similar MD MSDs. Dwell times by 
-%  ethylene glycol are shorter as shown by its larger $\alpha_d$ and $\lambda$ values. Both
+%  ethylene glycol are shorter as shown by its larger $\alpha$ and $\lambda$ values. Both
 %  solutes make similarly sized hops with hop distributions that are relatively close 
@@
 %  significantly slowed while they are in the tail region (mode 2) where long dwell times
-%  are more probable and hops are smaller (smaller $\alpha_d$). 
+%  are more probable and hops are smaller (smaller $\alpha$). 
 % BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
@@
 %  insight than the 1 mode model. It is clear that solutes are significantly slowed while
-%  they are in the tail region where long dwell times are more probable (lower $\alpha_d$)
+%  they are in the tail region where long dwell times are more probable (lower $\alpha$)
 %  and hops are smaller (smaller $\sigma$).  
 %  Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
-%  heavy tailed relative to ethylene glycol which has an $\alpha_d$ more consistent 
+%  heavy tailed relative to ethylene glycol which has an $\alpha$ more consistent 
 %  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
@@
   in the AD models, the $\beta$ parameter is only a function of $H$ and not dependent on
-  dwell times ($\alpha_d$, $\lambda$) or hop lengths ($\sigma$). The MSDDM is fundamentally similar to 
+  dwell times ($\alpha$, $\lambda$) or hop lengths ($\sigma$). The MSDDM is fundamentally similar to 
   the AD model in that one makes correlated draws from a hop distribution. Therefore,
@@
   The values of $c$ are directly related to the magnitude of solute flux and, where
-  applicable, are functions of $\sigma$, $\alpha_d$, $\lambda$ and $\alpha_h$. 
+  applicable, are functions of $\sigma$, $\alpha$, $\lambda$ and $\alpha_h$. 
   In Figure~\ref{fig:c_parameters}, we plot the $c$ values measured
@@
   Figure~\ref{fig:c_influence} we demonstrate that decreased dwell times
-  (increased $\alpha_d$), increased hop lengths (increased $\sigma$), cutting off the
+  (increased $\alpha$), increased hop lengths (increased $\sigma$), cutting off the
   dwell time distribution at shorter times (increased $\lambda$) and decreased tail 
@@
 %  We showed earlier that $\beta$ is not a
-%  function of $\sigma$ or $\alpha_d$, therefore dwell times and hop lengths must
+%  function of $\sigma$ or $\alpha$, therefore dwell times and hop lengths must
 %  influence $c$. In fact, any parameter which acts to modify the rate at which 
@@
   which increase the rate of solute displacement result in larger values of $c$. 
-  To test the dependence of $c$ on $\alpha_d$, $\sigma$, $H$ and $\lambda$, we chose a 
+  To test the dependence of $c$ on $\alpha$, $\sigma$, $H$ and $\lambda$, we chose a 
   single set of parameters, representative of solutes parameterized by the sFBMcut AD model,
@@
   same base parameter set. Therefore, the middle bars for these four 4 parameters are 
-  generated from the same set of parameters. Decreased dwell times (increased $\alpha_d$),
+  generated from the same set of parameters. Decreased dwell times (increased $\alpha$),
   increased hop lengths (increased $\sigma$), and a lower cut-off to the dwell time
   distribution (increased $\lambda$) lead to increases in $c$. $c$ responds linearly
-  to increases in $\sigma$ and $\lambda$ and non-linearly to $\alpha_d$. The data 
+  to increases in $\sigma$ and $\lambda$ and non-linearly to $\alpha$. The data 
   suggests that the $c$ parameters do not depend on hop anti-correlation ($H$). To test 

### 2020-01-08 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Fixed reference to main text
Consolidating

@@
 
-\externaldocument[M-]{Draft}
+\externaldocument[M-]{Final_Draft}
 
@@
   Analagous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
-  Figures~\ref{fig:GCL_anticorrelated_hops}--\ref{fig:MET_anticorrelated_hops} 
-  demonstrate that all solutes exhibit the same kind of anti-correlated hopping
-  and trapping behavior.
+  Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the
+  same kind of anti-correlated hopping and trapping behavior.
 
@@
   \centering
-  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
-  % /figures/solute_trajectories.py
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
-  \caption{}\label{fig:GCL_solute_trajectories}
-  \end{subfigure}
-  % Next 3: /figures/distributions_sfbm.py
-  \begin{subfigure}{0.45\textwidth}
+  % /figures/distributions_sfbm.py
+  \begin{subfigure}{0.3\textwidth}
   \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.3\textwidth}
   \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.3\textwidth}
   \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
@@
   \end{subfigure}
-  \caption{For ethylene glycol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
-  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions. 
-  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
-  in the main text for a more detailed discussion.}\label{fig:GCL_anticorrelated_hops}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
+  \caption{}\label{fig:ACH_hop_distribution_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
+  \caption{}\label{fig:ACH_powerlaw}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
+  \caption{}\label{fig:ACH_hop_acf}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
+  \caption{}\label{fig:MET_hop_distribution_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
+  \caption{}\label{fig:MET_powerlaw}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
+  \caption{}\label{fig:MET_hop_acf}
+  \end{subfigure}
+  \caption{Hop length distributions, dwell time distributions and hop autocorrelation functions
+  respectively for ethylene glycol (a-c), acetic acid (d-f) and methanol (g-i).
+  See Section~\ref{M-section:AD_parameterization} of the main text for a more detailed discussion.
+  }\label{fig:anticorrelated_hops}
+  \end{figure}
+
+  \newpage
+
+  \section{AD model MSD Predictions with Pure Power Law Dwell Times}\label{section:pure_power_law}
+
+  When we use a pure power law distribution to parameterize the dwell time 
+  distributions of the 1 and 2 mode AD models, the MD MSDs are severely 
+  under-predicted because we are incorporating dwell times on the order of 
+  the simulation length into simulated trajectories 
+  (see Figure~\ref{fig:anomalous_msds_bothmode}). The parameters of the pure power law 
+   distribution are included in Figure~\ref{fig:pure_power_law_params}.
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{bothmode_msd_comparison_URE.pdf}
+  \caption{Urea}\label{fig:bothmode_msd_comparison_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{bothmode_msd_comparison_GCL.pdf}
+  \caption{Ethylene Glycol}\label{bothmode_msd_comparison_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{bothmode_msd_comparison_MET.pdf}
+  \caption{Methanol}\label{fig:bothmode_msd_comparison_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{bothmode_msd_comparison_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:bothmode_msd_comparison_ACH}
+  \end{subfigure}
+  \caption{When we do not apply an exponential cut-off to the power law
+  distribution of dwell times,  MSDs are consistently under-predicted by the
+  AD model.
+  }\label{fig:anomalous_msds_bothmode}
   \end{figure}
@@
   \centering
-  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
-  % /figures/solute_trajectories.py
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
-  \caption{}\label{fig:ACH_solute_trajectories}
-  \end{subfigure}
-  % Next 3: /figures/distributions_sfbm.py
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
-  \caption{}\label{fig:ACH_hop_distribution_comparison}
+  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
+  \caption{}\label{fig:1mode_AD_dwells}
   \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
-  \caption{}\label{fig:ACH_powerlaw}
+  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
+  \caption{}\label{fig:2mode_AD_dwells}
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
-  \caption{}\label{fig:ACH_hop_acf}
-  \end{subfigure}
-  \caption{For acetic acid: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
-  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions.
-  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
-  in the main text for a more detailed discussion.}\label{fig:ACH_anticorrelated_hops}
-  \end{figure}
-
-  \begin{figure}
-  \centering
-  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
-  % /figures/solute_trajectories.py
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{MET_trajectories.pdf}
-  \caption{}\label{fig:MET_solute_trajectories}
-  \end{subfigure}
-  % Next 3: /figures/distributions_sfbm.py
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
-  \caption{}\label{fig:MET_hop_distribution_comparison}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
-  \caption{}\label{fig:MET_powerlaw}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
-  \caption{}\label{fig:MET_hop_acf}
-  \end{subfigure}
-  \caption{For methanol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
-  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions.
-  See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
-  in the main text for a more detailed discussion.}\label{fig:MET_anticorrelated_hops}
+  \caption{We can parameterize the dwell time distribution in two ways: as a pure
+  power law (P($\alpha$)) and as a power law with an exponential cut-off (P($\alpha$, $\lambda$)).
+  Pure power laws have an infinite variance which allows extremely long dwell
+  times to be sampled (see Figure~\ref{fig:anomalous_msds_bothmode}.
+  }\label{fig:pure_power_law_params}
   \end{figure}
@@
   \section{Stationarity of Solute Trajectories}\label{section:msd_comparison}
+
+  We evaluated the predictive capabilities of the AD modeling approach by training
+  the model parameters on the first half of the equilibrated MD trajectory data and
+  then comparing the MSD calculated from AD model realizations to the MSD calculated
+  from the second half of the equilibrated MD trajectory data. This metric is
+  only meaningful if the ensemble of solute trajectories is stationary. In 
+  Figure~\ref{msd_comparison}, we show that urea and acetic acid show acceptable
+  stationary behavior while methanol and ethylene glycol do not.
 
@@
   \end{figure}
+
+  We validated both the 1 and 2 mode AD models with urea and acetic acid, since their
+  trajectories appear stationary. The MSDs resulting from 1000 realizations of the AD
+  model are shown in Figure~\ref{fig:train_test}. We consider the model's prediction 
+  to match well if the MSD lies within the 1$\sigma$ confidence intervals of the MD MSDs.
+  We also look for qualitative agreement in the shape of the curves.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
+  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
+  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
+  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
+  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
+  \end{subfigure} 
+  %MRS6: I'm not sure I see red in urea.  Is the uncertainty that low?
+  %BJC6: I think red and orange are directly on top of each other with same error bars
+  \caption{In most cases, when using power laws with exponential cut-offs 
+  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
+  the first half of the equilibrated data lie within the 1$\sigma$ confidence
+  intervals of the MD MSD curves generated from the second half of the equilibrated
+  solute data. The models which use pure power laws systematically under-predict
+  the MD MSD curves. Over and under-estimated curvature of the of urea and acetic acid's 
+  MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
+  under-predicted at long timescales and those of acetic acid to be under-predicted
+  at short timescales.}\label{fig:train_test}
+  \end{figure}
+
+  The models are capable of reasonably predicting the MD MSD values of the second
+  half of the solute trajectories based on parameters generated from the first half
+  when the dwell time distributions are parameterized by a power law with an 
+  exponential cut-off. At long timescales, the MSD of Urea is under-predicted 
+  for both the 1 and 2 mode models with the same true of acetic acid on short 
+  timescales. Without truncation of the power law distribution, the MD 
+  MSDs are underestimated in all cases because dwell times on the order of the
+  MD simulation length are sampled and incorporated into the simulated anomalous
+  diffusion trajectories. Considering the longest observed dwell time among all
+  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
+  %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
+  %intervals of the MD MSD curves, they appear to lie systematically below the mean. 
+  %It is not clear whether this is a consistent feature of the AD model since we 
+  %only used 2 solutes for this analysis.
+
+%  We also observe that simulated AD trajectories which draw from a L\'evy stable 
+%  distribution generally predict higher MSDs. The heavy tails of the distribution 
+%  incorporate large jumps more frequently into the trajectories.
+
+  From a qualitative perspective, the models only have moderate success at predicting
+  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
+  the error in the predicted MSD magnitudes. The curves predicted for Urea with both 1 
+  and 2 modes appear to have too much curvature, which causes it to under-predict the 
+  MSD at long timescales, while those of acetic acid lack curvature, leading the
+  AD model to under-predict the MSD at short timescales.
+
+  The under-estimate of Urea's MSD at long timescales is due to long timescale
+  positional anti-correlation which may not be present in the molecularly 
+  detailed simulations of the system. The 
+  %MRS6: I'm not following whether or not there should be positional anti-correlation.  I was thinking there should be,
+  %but perhaps I'm misunderstanding something here? 
+  persistent curvature of the predicted MSD curves is a direct consequence of 
+  the Hurst parameter. Without anti-correlation, the process would be 
+  a pure CTRW for which one would expect the time averaged MSD curves to become 
+  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
+  positional correlation is lost which would manifest as a transition from a sub-linear
+  to linear MSD curve. A solution for more accurately modeling this behavior in  
+  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}
+
+  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
+  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
+  because the Hurst parameter is challenging to quantify, especially with a relatively 
+  small amount of data (see Section~\ref{method:sfbm} for further discussion of this 
+  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
+  but also lower the predicted MSD meaning we are either underestimating the width of
+  the hop length distribution, favoring longer dwell times, or both.
+
+  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
+  a real system, positional anti-correlation may dissipate after a sufficiently long 
+  time lag, dependent on the solute being studied. Second, it is difficult to reliably
+  parameterize the Hurst parameter which is important for accurately describing the 
+  curvature of the solute MSDs.
+
+  This analysis also suggests that working with only half of the data we collected
+  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
+  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
+  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
+  sFLMcut), but still appear to systematically under-predict the mean. We may be
+  operating on the border of the minimum amount of data required to accurately 
+  parameterize the AD model. Longer simulations and more independent trajectories may
+  be necessary. Therefore, in the next section we will work with parameters fit to the
+  full equilibrated portion of the solute trajectories, doubling the data.
+
+%MRS6: My instinct is to only show the graphs of the full model, with validation graphs shown in the supporting.
+We can talk about this.
+We do what the focus to be on what we can learn physically.
+The discussion gets pretty repetitive.
+
+%MRS6: be a bit clearer about how the MD MSD error bounds are calculated.  That becomes important for determining how accurate the modeling is. .
+
+%  However, in the case of acetic acid, this may only happen because the 
+%  Hurst parameter is overestimated. It appears we are operating on the border of the
+%  minimum amount of data required to accurately parameterize the AD model. Longer
+%  simulations and more independent trajectories may be necessary. Therefore, in 
+%  the next section we will work with parameters fit to the full equilibrated portion
+%  of the solute trajectories, doubling the data.
+
+%  This brief analysis highlights some of the shortcomings of the AD model. So far, we have 
+%  shown that it does a reasonable job of approximating the magnitude of the MD-MSD
+%  after a 500 ns time lag, but the shape can sometimes be qualitatively wrong because of
+%  inaccurate Hurst parameters. In the case of acetic acid, a poorly measured $H$, but 
+%  accurate prediction of the magnitude of the MSD after 500 ns, may mask underlying 
+%  problems with the parameters of the hop length and dwell time distributions. Acetic
+%  acid has the lowest MSD of the solutes studied, therefore these issues may be resolved
+%  by longer simulations.
+
+  %BJC4: comment here about the length of time simulations need to be run in 
+  % order to get reliable data
+  % Or maybe a little later since acetic acid, although stationary
+  % comment on acetic acid's trajectory shape.
 
@@
   trajectories and used them to generate realizations of our MSDDM model. The states
-  are defined in Table~\ref{table:states} except state T which describes the transition
+  are defined in Table~\ref{M-table:states} of the main text except state T which describes the transition
   emissions.}\label{table:msddm_params}

### 2020-01-08 Ben_Manuscripts/stochastic_transport/figures/1mode_AD_hops.py

@@ -12,7 +12,8 @@ import matplotlib.patches as mpatches
 root_dir = "/home/bcoscia/Documents/Gromacs/Transport/NaGA3C11"
 sol = ['URE', 'GCL', 'MET', 'ACH']
 colors = {'URE':'xkcd:blue', 'GCL':'xkcd:orange', 'MET':'xkcd:green', 'ACH':'xkcd:magenta'}
-colors = {'sigma_normal': 'xkcd:blue', 'sigma_levy': 'xkcd:gold', 'alpha': 'xkcd:orangered'}
+colors = {'sigma_normal': (0.667, 0.361, 0.224), 'sigma_levy': (0.165, 0.306, 0.431), 'alpha': (0.361, 0.588, 0.196)}
+colors = {'sigma_normal': 'xkcd:magenta', 'sigma_levy': 'xkcd:orange', 'alpha': 'xkcd:blue'}
 names = {'URE': 'urea', 'GCL': 'ethylene glycol', 'MET': 'methanol', 'ACH': 'acetic acid'}
 names2 = ['urea', 'ethylene\nglycol', 'methanol', 'acetic\nacid']
 bar_width = 0.2

### 2020-01-08 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Condensing

@@
 
-  \section{Mean first passage time simulations}\label{section:mfpt}
-
-%  We validated our approach to simulating trajectory realizations by testing
-%  it against analytical solutions to the mean first passage time of a Brownian
-%  particle with 2 absorbing boundaries.
-  \subsection*{Analytical fits to MFPT distributions}
+  \section*{Analytical fits to MFPT distributions}\label{section:mfpt_fits}
 
@@
 
+  \newpage
+
+  \section{Explanation of Under-Estimated MSDDM $\beta$ Values}\label{section:beta_estimates}
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.43\textwidth}
+  \includegraphics[width=\textwidth]{beta_hurst.pdf}
+  \caption{}\label{fig:beta_hurst}
+  \end{subfigure}
+  \begin{subfigure}{0.52\textwidth}
+  \includegraphics[width=\textwidth]{beta_parameters.pdf}
+  \caption{}\label{fig:beta_parameters}
+  \end{subfigure}
+  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
+  %MRS6: should try to lead with what the overall results/conclusions are.
+What does it mean that parameters are larger or smaller?
+What should the reader take from the discussion?
+Should it be in supportinig?
+  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
+  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
+  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
+  sub-trajectories between state transitions decorrelate transitional hops and because
+  our FLM simulation procedure does not accurately correlate hops after long time lags. 
+  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
+  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
+  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
+  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
+  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
+  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
+  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
+  \end{figure}
+
   \clearpage

### 2020-01-09 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Fixed figure references

@@
   only meaningful if the ensemble of solute trajectories is stationary. In 
-  Figure~\ref{msd_comparison}, we show that urea and acetic acid show acceptable
+  Figure~\ref{fig:msd_comparison}, we show that urea and acetic acid show acceptable
   stationary behavior while methanol and ethylene glycol do not.
@@
   because the Hurst parameter is challenging to quantify, especially with a relatively 
-  small amount of data (see Section~\ref{method:sfbm} for further discussion of this 
+  small amount of data (see Section~\ref{M-method:sfbm} of the main text for further discussion of this 
   challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
@@
 
+  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
+  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
+  Turning first to the model itself, we have designed it to ensure that the magnitude of the
+  hops in the series of transitions between states are anti-correlated from start to finish. 
+  This assumes that the transition correlation structure is unaffected by the
+  sub-trajectories between each state transition. Each time a state transition occurs, one
+  must initialize a new time series sub-trajectory with its own correlation structure. 
+  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
+  %in each state is relatively short making the accuracy of the correlation structure 
+  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
+  %$\sigma$ in trapped states. 
+  Since we add the transitional hop lengths to each end of
+  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
+  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
+  MSDDM to completely immobilize particles except when they transition between states. 
+  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
+  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
+  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
+  To generate the curves in Figure~\ref{M-fig:flux_curves_msddm}, we needed to correlate 
+  25--1000 times more hops than for the MSD predictions in Figure~\ref{M-fig:msddm_performance}. 
+  In short, it is computationally infeasible to use enough terms to accurately incorporate
+  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
+  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
+  fractional Brownian motion, for which we have an exact simulation method, in place of 
+  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
+  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
+  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
+  of FLM.
+
   \begin{figure}[h]

### 2020-01-12 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Added missing tex file

--- 2020-01-08 Ben_Manuscripts/stochastic_transport/Draft.tex
@@
 \usepackage{array}
+
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
@@
 \newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
+
+\usepackage{titlesec}
+\titleformat{\subsubsection}[runin]
+  {\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}
 
@@
 
+  %BJC6: I could make abstract margins smaller
   \begin{abstract}
@@
   a power law of the form: 
-  %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
   \begin{equation} 
@@
   \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
+  \label{eqn:tamsd}
   \end{equation}
@@
   average, it is a more statistically robust measure of the average distance a 
-  solute travels over time. 
-  % MRS6: does it correspond properly to the physical situation of entry into the 
-  % pore of new particles at each unit time?
-  % BJC6: no, but neither does ensemble
-  Although theoretically possible, we do not use the ensemble averaged MSD to 
-  calculate $\alpha$ because we can extract the same parameter with higher 
-  precision using the dwell time distributions as described below.
+  solute travels over time. Although theoretically possible, we do not use the 
+  ensemble averaged MSD to calculate $\alpha$ because we can extract the same 
+  parameter with higher precision using the dwell time distributions as described below.
 
@@
   parameter we calculated by maximizing the likelihood function: 
+  %BJC6: I could move these MLE equations to Supporting
   \begin{equation}
@@
   In practical applications, the heavy tail of power law distributions can result in 
-  arbitrarily long dwell times that are never observed in MD simulations. We cannot
-  observe dwell times longer than the length of a single trajectory. 
+  arbitrarily long dwell times that are never observed in MD simulations. 
+  %We cannot observe dwell times longer than the length of a single trajectory. 
   In order to directly compare our anomalous diffusion model to finite-length MD 
@@
   When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
-  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
+  and when $H > 0.5$, one observes positive correlation between hops. 
+  %BJC6: I could move the following to supporting and keep last sentence.
+  There are many methods
   for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
@@
 
-  Assuming hops are correlated, solute behavior may be described by subordinated 
+  For correlated hops, solute behavior may be described by subordinated 
   fractional L\'evy motion (sFLM). The Hurst parameter can again be used to describe
@@
   Our second, two mode model assigns a set of parameters to each of 2 modes based
-  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
-  %MRS4: some justification on why 0.75 vs. any other cutoff.
-  %BJC4: I justified sentence after next. 
-  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
-  We determined this cut-off by maximizing the difference in dynamical behavior as 
+  on the solute's radial location. We define the first mode as the pore region, 
+  defined as less than 0.75 nm from any pore center. All else are in the second mode, the
+  tail region. We determined this cut-off by maximizing the difference in dynamical behavior as 
   described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
@@
   between fixed length sFBM simulations.
-  % BJC4: removed following sentence because I talk about aging above
-  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
-  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
-  We reported the time-averaged MSD up to a 1000 ns time lag corresponding 95\% confidence
+
+  %BJC6: added this. Not sure how much detail is necessary
+  We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
+  and AD model trajectories then estimated their uncertainty using statistical 
+  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute trajectories,
+  where $n$ is the number of independent trajectories, with replacement from the 
+  ensemble of trajectories and then calculated the MSD of the subset. We reported 
+  the time-averaged MSD up to a 1000 ns time lag with corresponding 95\% confidence
   intervals.
@@
 
-  %BJC4: already said this earlier
-%  We used a single Hurst parameter to describe
-%  correlation between hops, independent of the solute's mode. Ideally, each mode
-%  would have its own Hurst parameter, but we did not observe enough long sequences
-%  of uninterrupted time spent in each mode with which to generate robust
-%  autocorrelation functions.
-
   %BJC3: not sure how to cite fbm
@@
   validation of the approach).
-  %MRS6: suggest in the supporting information describe what measure was used to determine that the algorithm sufficiently and reasonably approxmiates.
+  % MRS6: suggest in the supporting information describe what measure was used to 
+  % determine that the algorithm sufficiently and reasonably approxmiates.
 
@@
   with transitions between states defined by a transition probability matrix, $T$,
-  which describes the conditional probability of jumping to a specific state given
+  which describes the conditional probability of moving to a specific state given
   the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
@@
 
-  %MRS4: here, be more explicit you are testing the validity of the Markovian approximation on the molecular data.
-  %BJC4: Tried to clarify in thesis statement. Let me know if you think it needs more
+  %BJC6: could defer most of this to supporting. 
   We verified the Markovianity of state transitions by solutes in our MD simulations 
@@
   %BJC5: I said the following earlier , but I still think it belongs
-  Hence why we refer to them as Markov State-Dependent Dynamical Models (MSDDMs).
+  Hence why we refer to them as Markov state-dependent dynamical models (MSDDMs).
 
@@
   time. To account for input concentration dependence of the flux, assuming that particles
-  are uncorrelated, one can multiply Equation~\ref{eqn:hill_relation} by the total number
+  are independent, one can multiply Equation~\ref{eqn:hill_relation} by the total number
   of particles to get the total flux. In the context of our work, the MFPT describes the
@@
   For computational reasons dependent on the model used, we simulated 1,000-10,000 trajectory
-  realizations, released at the pore entrance ($z=0$). In the case of 
+  realizations, released at the pore entrance ($z=0$). 
+  %BJC6: next two sentences might not be necessary  
+  In the case of 
   uncorrelated hops, one can continuously draw from the hop length distribution until 
@@
 
+  %BJC6: could probably remove this paragraph.
   We calculated the expected value of analytical fits to the passage time distributions
@@
 
-  %BJC4: Not sure if I should start by commenting on the stationarity of the 
-  %solute trajectories. I talk about it when I start validating with the train/test procedure.
-
-%  \subsection{Stationarity of Solute Trajectories}\label{section:stationarity}
-%  %BJC4: Maybe re-theme the section: applicability of model
-%  
-%  Before applying the model, it is important to analyze the MD trajectories
-%  themselves in order to understand what conclusions one could reasonably to 
-%  draw by applying these models. 
-%  
-%  %BJC4: this might belong with validation.
-%  We observe that in many cases, the distribution of solutes within the membrane
-%  evolves slowly with time. We defined the perceived equilibration time point 
-%  for each solute based on the time at which the number of solutes inside the
-%  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
-%  solute behavior after equilibration on the $\mu$s timescale. In Table \_\_, we compare the MSD of the 
-%  solutes calculated using trajectory data from the first and second halves of the
-%  equilibrated simulation time. Ethylene glycol and methanol, show considerable
-%  differences in their MSDs. Although the MSD calculated from both halves of the 
-%  acetic acid trajectories are similar, their shapes are considerably different 
-%  (see SI). Urea is the only solute in this study that demonstrates satisfactory
-%  stationarity on the 5 $\mu$s timescale.
-%  
-%  The non-stationary behavior of each solute presents itself in different ways.
-%  On average, methanol molecules in the tails appear to be drifting further 
-%  away from the pore center with time. Ethylene glycol appears to experience an
-%  increased incidence of long trapping times. The partition of acetic acid 
-%  between the pores and tails oscillates slowly over time. These problems probably
-%  cannot be addressed without more simulation time or additional solute trajectories. 
-%  
-%  In light of these observations, we chose to demonstrate the performance and insights
-%  that could be gained from our models using all of solutes with complete data sets
-%  collected after the perceived equilibration time. However, we only use urea to 
-%  validate the model's predictive power and to estimate solute flux.
-%    
-%  There are a couple of ways to address this issue in the long term. The simplest
-%  approach is to run the MD simulations longer. This option is likely not feasible
-%  because the equilibration timescale in these systems is unknown for most of 
-%  the solutes in the study, even after consider computational effort. A more 
-%  sustainable approach, which would help screen any solute of interest, would 
-%  require us to learn the equilibrium distribution of solutes in the membrane
-
   \subsection{Anomalous Diffusion Modeling}\label{section:sFBM}
@@
   The evidence suggests that solutes in this system can be well-modeled by subordinated
-  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use urea to
-  support this claim. Analogous figures for all other solutes are presented in the Supporting
-  Information, Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops}.
-  The solutes clearly perform jumps after periods of relative
-  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
-  of jump lengths and power law distribution of dwell times are both characteristic of 
-  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
-  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
-  CTRW. We believe the subordinated process is FBM or FLM because their analytical correlation 
-  structures are close to those observed in our simulations (Figure~\ref{fig:hop_acf}). Fractional
-  motion is common in crowded viscoelastic environments where movement is highly influenced by
-  the movement of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
-  %The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
-  %summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
+  fractional Brownian motion. In Figure~\ref{fig:solute_trajectories}, we plotted representative
+  trajectories for each solute. They are characterized by intermittent hops between
+  periods of entrapment. The near-Gaussian distribution of jump lengths and power law 
+  distribution of dwell times are both characteristic of CTRWs 
+  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
+  anti-correlation between hops suggests a fractional diffusion process is subordinate 
+  to the CTRW. We believe the subordinated process is FBM or FLM because their analytical
+  correlation structures are close to those observed in our simulations (Figure~\ref{fig:hop_acf}).
+  Fractional motion is common in crowded viscoelastic environments where movement is highly 
+  influenced by the movement of surrounding components, such as monomer tails in our 
+  case.~\cite{ernst_fractional_2012}
 
@@
   \centering
-  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
   % /figures/solute_trajectories.py
@@
   \includegraphics[width=\textwidth]{URE_trajectories.pdf}
-  \caption{}\label{fig:solute_trajectories}
+  \caption{Urea}\label{fig:URE_trajectories}
   \end{subfigure}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
+  \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
+  \caption{Ethylene glycol}\label{fig:GCL_trajectories}
+  %BJC6: ^^ Should I capitalize glycol?
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{MET_trajectories.pdf}
+  \caption{Methanol}\label{fig:MET_trajectories}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
+  \caption{Acetic acid}\label{fig:ACH_trajectories}
+  \end{subfigure}
+  \caption{Representative trajectories generated from each solute exhibit hops 
+  between periods of entrapment, characteristic of a CTRW. Solute dynamics show
+  radial dependence. The longest periods of entrapment typically occur when 
+  solutes drift far from the pore center and into the tails.
+  }\label{fig:solute_trajectories}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  % Next 3: /figures/sfbm_distributions
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
   \caption{}\label{fig:hop_distribution_comparison}
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
@@
   \end{subfigure}
-  \caption{(a) Urea exhibits hops between periods of entrapment, characteristic of a CTRW. 
-  (b) The distribution of hop lengths fits well to a Gaussian as well as a more general L\'evy 
-  stable distribution. The L\'evy stable distribution does a better job of capturing the 
-  heavier tails and increased density near 0. (c) The distribution of dwell times is fit
-  well by a power law but it may over-estimate the probability density at long dwell times.
-  A power law truncated with an exponential cut-off may better describe the probability of
-  long dwell times in our simulations. (d) The hops are negatively correlated to their previous
-  hop. In combination, (a) -- (d) support modeling solutes as subordinated fractional Brownian
-  and L\'evy motion. The behavior shown by urea in this figure is common to all solutes in this study (see
-  Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops} of the
-  Supporting Information).}\label{fig:anticorrelated_hops}
-  %MRS4: are there similar figures in the supporting information.
-  %BJC4: added
-  %MRS6: I'm wondering if the other plots should be in the main text.  They are part of the core of the paper, showing that the modeling is reasonable. 
+  \caption{Using urea as an example, (a) the distribution of hop lengths fits well to 
+  a Gaussian as well as a more general L\'evy stable distribution. The L\'evy stable
+  distribution does a better job of capturing the heavier tails and increased density
+  near 0. (b) The distribution of dwell times is fit well by a power law but it may 
+  over-estimate the probability density at long dwell times. A power law truncated with
+  an exponential cut-off may better describe the probability of long dwell times in 
+  our simulations. (c) The hops are negatively correlated to their previous hop. In
+  combination, (a) -- (c) support modeling solutes as subordinated fractional Brownian
+  and L\'evy motion. All other solutes show similar distributions and autocorrelation
+  function (see Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
+  }\label{fig:anticorrelated_hops}
   \end{figure}
+
+%  \begin{figure}
+%  \centering
+%  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
+%  % /figures/solute_trajectories.py
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{URE_trajectories.pdf}
+%  \caption{}\label{fig:solute_trajectories}
+%  \end{subfigure}
+%  % Next 3: /figures/sfbm_distributions
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
+%  \caption{}\label{fig:hop_distribution_comparison}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
+%  \caption{}\label{fig:powerlaw}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
+%  \caption{}\label{fig:hop_acf}
+%  \end{subfigure}
+%  \caption{(a) Urea exhibits hops between periods of entrapment, characteristic of a CTRW. 
+%  (b) The distribution of hop lengths fits well to a Gaussian as well as a more general L\'evy 
+%  stable distribution. The L\'evy stable distribution does a better job of capturing the 
+%  heavier tails and increased density near 0. (c) The distribution of dwell times is fit
+%  well by a power law but it may over-estimate the probability density at long dwell times.
+%  A power law truncated with an exponential cut-off may better describe the probability of
+%  long dwell times in our simulations. (d) The hops are negatively correlated to their previous
+%  hop. In combination, (a) -- (d) support modeling solutes as subordinated fractional Brownian
+%  and L\'evy motion. The behavior shown by urea in this figure is common to all solutes in this study (see
+%  Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops} of the
+%  Supporting Information).}\label{fig:anticorrelated_hops}
+%  %MRS4: are there similar figures in the supporting information.
+%  %BJC4: added
+%  %MRS6: I'm wondering if the other plots should be in the main text.  They are part of the core of the paper, showing that the modeling is reasonable. 
+%  \end{figure}
 
@@
   the MLE fits of both on top of urea's hop length distribution in 
-  Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a better
-  job capturing the somewhat heavy tails and high density near 0 of the hop length distribution.
+  Figure~\ref{fig:hop_distribution_comparison}. 
+  %BJC6: I say the next sentence in plot
+  The L\'evy distribution does a better job capturing the somewhat heavy tails and 
+  high density near 0 of the hop length distribution.
   However, since there are no known exact simulation techniques for generating 
@@
   When we do not truncate the dwell time distribution, the trajectories tend to 
-  incorporate very long dwell times as shown by the sFBM and sFLM models.
+  incorporate very long dwell times as shown by the sFBM and sFLM models. Predictions
+  made with these models consistently under-predict the MD MSDs (see 
+  Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supporting Information), therefore 
+  we will not include the pure sFBM or sFLM models in the remainder of our analysis.
+
+%  \begin{figure}
+%  \centering
+%  %plot_ad_realization.py
+%  \includegraphics[width=0.5\textwidth]{ad_realizations_1mode.pdf}
+%  \caption{Simulations of 1 mode AD model trajectories for urea display qualitatively
+%  similar hopping and trapping behavior to that shown in Figure~\ref{fig:solute_trajectories}. 
+%  Dwell times appear exaggerated in the sFBM and sFLM models because the power law dwell
+%  time distributions are not truncated and have infinite variance.
+%  %Analogous plots are shown for other solutes
+%  %MRS6: I don't think the comparison between the cut and no cut are that interesting for the main text.  Move to supporting?
+%  %MRS6: comparisons between modeled and actual trajectories side by side would be more interesting. 
+%  %BJC5: todo: add plots to SI. Show I add a 2 mode model plot?
+%  %and the 2 mode model in the Supporting Information. 
+%  }\label{fig:ad_eyetest}
+%  \end{figure}
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{ad_realizations_1mode.pdf}
-  \caption{Simulations of 1 mode AD model trajectories for urea display qualitatively
-  similar hopping and trapping behavior to that shown in Figure~\ref{fig:solute_trajectories}. 
-  Dwell times appear exaggerated in the sFBM and sFLM models because the power law dwell
-  time distributions are not truncated and have infinite variance.
+  %plot_ad_realization.py
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{ad_realizations_1mode.pdf}
+  \caption{}\label{fig:ad_realizations_1mode}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{ad_realizations_URE_sFBMcut_stacked.pdf}
+  \caption{sFBMcut}\label{fig:ad_realizations_sFBMcut_stacked}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{ad_realizations_URE_sFLMcut_stacked.pdf}
+  \caption{sFLMcut}\label{fig:ad_realizations_sFLMcut_stacked}
+  \end{subfigure}
+  \caption{(a) Simulated urea trajectories generated by each variation on the 1 mode AD model 
+  display qualitatively similar hopping and trapping behavior to that shown in Figure~\ref{fig:solute_trajectories}. 
+  Dwell times are exaggerated in the sFBM and sFLM models because the power law dwell
+  time distributions are not truncated and have infinite variance. In (b) and (c) we 
+  compare additional trajectories simulated with the sFBMcut and sFLMcut models (blue) to
+  MD solute trajectories (black).  
   %Analogous plots are shown for other solutes
@@
 
-  \subsubsection{Model validation on stationary trajectories}\label{section:sfbm_validation}
-
-  We evaluated the predictive capabilities of the AD modeling approach by training
-  the model parameters on the first half of the equilibrated MD trajectory data and
-  then comparing the MSD calculated from AD model realizations to the MSD calculated
-  from the second half of the equilibrated MD trajectory data. This metric is
-  only meaningful if the ensemble of solute trajectories is stationary.
-
-  We observe that in many cases, the distribution of solutes within the membrane
-  evolves slowly with time. We defined the perceived equilibration time point 
-  for each solute based on the time at which the number of solutes inside the
-  pores and tails stabilized (Figure~\ref{S-fig:equilibration}). Nonetheless, we observe evidence of non-stationary
-  solute behavior after equilibration, on the $\mu$s timescale. In Table~\ref{table:stationarity},
-  we compare the MSD of the solutes calculated using trajectory data from the 
-  first and second halves of the ``equilibrated" simulation time. Ethylene glycol 
-  and methanol show considerable differences in their MSDs. Urea and acetic acid
-  appear to demonstrate satisfactory stationarity. The shapes of their MSDs curves
-  are also very similar (see Figure~\ref{S-fig:msd_comparison} of the Supporting
-  Information).
+  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}
+
+%  We evaluated the predictive capabilities of the AD modeling approach by training
+%  the model parameters on the first half of the equilibrated MD trajectory data and
+%  then comparing the MSD calculated from AD model realizations to the MSD calculated
+%  from the second half of the equilibrated MD trajectory data. This metric is
+%  only meaningful if the ensemble of solute trajectories is stationary.
+
+  We observe that in some cases, solute trajectories extracted from our MD simulations
+  display non-stationary behavior. We defined the perceived equilibration time point for
+  each solute based on the time at which the number of solutes inside the pores and tails
+  stabilized (Figure~\ref{S-fig:equilibration}). Nonetheless, we observe evidence of 
+  non-stationary solute behavior after the perceived equilibration, on the $\mu$s 
+  timescale. In Table~\ref{table:stationarity}, we compare the MSD of the solutes 
+  calculated using trajectory data from the first and second halves of the 
+  ``equilibrated" simulation time. Ethylene glycol and methanol show considerable 
+  differences in their MSDs. Urea and acetic acid appear to demonstrate satisfactory
+  stationarity. The shapes of their MSDs curves are also very similar (see 
+  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
 
@@
 
-  %MRS6: you don't say what is in the paragraphs.
   \end{tabular}
-  \caption{In order to be considered stationary, the MSD of the ensemble of solute trajectories
-  should be the same independent of the portion of equilibrated trajectory that is
-  analyzed. The MSD values in this table are averages taken after a 500 ns time lag, 
-  calculated independently from the first and second halves of the equilibrated
-  solute trajectories. Urea and acetic acid both appear to satisfy the stationarity
-  criteria, while ethylene glycol and methanol show significantly smaller MSDs 
-  when calculated from the second half of the equilibrated trajectories.}\label{table:stationarity}
+  \caption{In order to be considered stationary, the MSD of the ensemble of solute 
+  trajectories should be the same independent of the portion of equilibrated 
+  trajectory that is analyzed. The MSD values in this table are averages taken 
+  after a 500 ns time lag, calculated independently from the first and second 
+  halves of the equilibrated solute trajectories. Urea and acetic acid both 
+  appear to satisfy the stationarity criteria, while ethylene glycol and methanol
+  show significantly smaller MSDs when calculated from the second half of the 
+  equilibrated trajectories.}\label{table:stationarity}
   \end{table}
 
-%  The non-stationary behavior of ethylene glycol and methanol present themselves
-%  in different ways. On average, methanol molecules in the tails appear to be 
-%  drifting further away from the pore center with time. Methanol's small size 
-%  significantly increases the volume of accessible structural space. Ethylene 
-%  glycol appears to experience an increased incidence of long trapping times. 
-%  These problems probably cannot be addressed without more simulation time or 
-%  additional solute trajectories.
-
-  Using the approach described above, we validated our 1 and 2 mode models with
-  urea and acetic acid, since their trajectories appear stationary. 
-  The MSDs resulting from 1000 realizations of the AD model are shown in 
-  Figure~\ref{fig:train_test}. We consider the model's prediction to match well if the
-  MSD lies within the 1$\sigma$ confidence intervals of the MD MSDs. We also
-  look for qualitative agreement in the shape of the curves.
-
+  % BJC6: These next two paragraphs are a bit awkward without the figure being present. Not sure what the best course of action is.
+  Given stationary data, the AD model has satisfactory predictive capabilities. In 
+  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized 
+  the AD model using the first half of the stationary solute equilibrated trajectories 
+  and then compared the model predictions to the MD MSD of the second of half 
+  of the stationary trajectories. In most cases, the model predictions fall within
+  the 1$\sigma$ confidence intervals of the MD MSD.
+
+  This brief analysis suggests that we may be operating on the border of the minimum 
+  amount of data required to accurately parameterize the AD model. Working with 
+  only half of the data we collected ($\sim$ 2 $\mu$s post-equilibration) may not
+  always be sufficient for extracting reliable parameter estimates. Therefore, for 
+  the remainder of this work, we will employ parameters fit to the entire
+  equilibrated portion of the solute trajectories.%, doubling the data.
+
+%  In most cases, 
+%  the magnitude of the MSD predictions after a 
+%  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
+%  sFLMcut), but still appear to systematically under-predict the mean.  Longer simulations and more independent trajectories may
+%  be necessary.
+
+  %BJC: say something about how more independent trajectories may not fix the problem
+  % because there are different features of the MSD curves on different timescales.
+
+  \subsubsection{Model predictions}\label{section:AD_all_data}
+
+  We obtain reasonable predictions of the MD simulated MSDs when we parameterize the AD 
+  model with all available data after the perceived equilibration time. Although we 
+  concluded that methanol and ethylene glycol trajectories may not yet be stationary, we 
+  include them in all analysis going forward because it is still instructive. 
+  The MSD curves generated from the 1 and 2 mode models are overlayed with the MD 
+  simulated MSDs for comparison in Figure~\ref{fig:anomalous_msds}. The associated 
+  parameters for the 1 and 2 mode models are presented in Figures~\ref{fig:1mode_parameters}
+  and~\ref{fig:2mode_parameters}.
+
+  %BJC6: combined 1 and 2 mode models. Easier to compare between and takes up less space. maybe a little cluttered with acetic acid.
   \begin{figure}
@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
-  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
+  \includegraphics[width=\textwidth]{bothmode_msd_comparison_URE.pdf}
+  \caption{Urea}\label{fig:bothmode_msd_comparison_URE}
   \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
-  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
+  \includegraphics[width=\textwidth]{bothmode_msd_comparison_GCL.pdf}
+  \caption{Ethylene Glycol}\label{fig:bothmode_msd_comparison_GCL}
   \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
-  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
+  \includegraphics[width=\textwidth]{bothmode_msd_comparison_MET.pdf}
+  \caption{Methanol}\label{fig:bothmode_msd_comparison_MET}
   \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
-  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
-  \end{subfigure} 
-  %MRS6: I'm not sure I see red in urea.  Is the uncertainty that low?
-  %BJC6: I think red and orange are directly on top of each other with same error bars
-  \caption{In most cases, when using power laws with exponential cut-offs 
-  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
-  the first half of the equilibrated data lie within the 1$\sigma$ confidence
-  intervals of the MD MSD curves generated from the second half of the equilibrated
-  solute data. The models which use pure power laws systematically under-predict
-  the MD MSD curves. 
-  %MRS6: be more specific when you say ``improper''. What is improper?
-Improper curvature of the MSD curves cause the magnitude of
-  the urea's predicted MSDs to be under-predicted at long timescales and those
-  of acetic acid to be under-predicted at short timescales.}\label{fig:train_test}
-  %MRS6: I'm not sure it makes sense to show the ``without cutoff'' lines here.  Maybe supporting?  
-  %MRS6: I'm just not sure it really pushes the paper forward to show more data that something you've shown
-  %MRS6: isn't likely to work earlier still isn't working. 
-  \end{figure}
-
-  The models are capable of reasonably predicting the MD MSD values of the second
-  half of the solute trajectories based on parameters generated from the first half
-  when the dwell time distributions are parameterized by a power law with an 
-  exponential cut-off. At long timescales, the MSD of Urea is under-predicted 
-  for both the 1 and 2 mode models with the same true of acetic acid on short 
-  timescales. Without truncation of the power law distribution, the MD 
-  MSDs are underestimated in all cases because dwell times on the order of the
-  MD simulation length are sampled and incorporated into the simulated anomalous
-  diffusion trajectories. Considering the longest observed dwell time among all
-  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
-  %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
-  %intervals of the MD MSD curves, they appear to lie systematically below the mean. 
-  %It is not clear whether this is a consistent feature of the AD model since we 
-  %only used 2 solutes for this analysis.
-
-%  We also observe that simulated AD trajectories which draw from a L\'evy stable 
-%  distribution generally predict higher MSDs. The heavy tails of the distribution 
-%  incorporate large jumps more frequently into the trajectories.
-
-  From a qualitative perspective, the models only have moderate success at predicting
-  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
-  the error in the predicted MSD magnitudes. The curves predicted for Urea with both 1 
-  and 2 modes appear to have too much curvature, which causes it to under-predict the 
-  MSD at long timescales, while those of acetic acid lack curvature, leading the
-  AD model to under-predict the MSD at short timescales.
-
-  The under-estimate of Urea's MSD at long timescales is due to long timescale
-  positional anti-correlation which may not be present in the molecularly 
-  detailed simulations of the system. The 
-  %MRS6: I'm not following whether or not there should be positional anti-correlation.  I was thinking there should be,
-  %but perhaps I'm misunderstanding something here? 
-  persistent curvature of the predicted MSD curves is a direct consequence of 
-  the Hurst parameter. Without anti-correlation, the process would be 
-  a pure CTRW for which one would expect the time averaged MSD curves to become 
-  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
-  positional correlation is lost which would manifest as a transition from a sub-linear
-  to linear MSD curve. A solution for more accurately modeling this behavior in  
-  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}
-
-  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
-  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
-  because the Hurst parameter is challenging to quantify, especially with a relatively 
-  small amount of data (see Section~\ref{method:sfbm} for further discussion of this 
-  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
-  but also lower the predicted MSD meaning we are either underestimating the width of
-  the hop length distribution, favoring longer dwell times, or both.
-
-%  Urea's curves appear to have
-%  close to the right amount of curvature at short timescales
-
-%  In general, the MSDs generated by our AD models appear
-%  close to linear at long time scales. This is expected behavior for time averaged 
-%  MSDs, especially when truncating the power law distribution of dwell times.
-%  \cite{molina-garcia_crossover_2018} The linearity of Urea's MD MSD curve is 
-%  consistent with that of the AD model, but the MD MSD of acetic acid appears to have considerable
-%  curvature.
-
-%  Acetic acid's MSD is under-predicted at short timescales but within error 
-%  of MD (using sFBMcut and sFLMcut models) after a 500 ns time lag. The curvature suggests that the 
-%  model under-estimates long timescale positional anti-correlation which points to an
-%  over-estimate of the Hurst parameter. This is not surprising because the Hurst 
-%  parameter is challenging to quantify, especially with a relatively small amount of 
-%  data (see Section~\ref{method:sfbm} for further discussion of this challenge).
-%  A more accurate measurement of $H$ would fix the shape of the MSD curve, but also
-%  lower the predicted MSD meaning we are either underestimating the width of the hop
-%  length distribution, favoring longer dwell times or both.
-  % BJC4: play around with this to see how to change shape of acetic acid curve. Hurst makes it arc more
-  % ctrwsim.py -alpha 0.08 -fix_time -hop fbm -H 0.34 -ntraj 100 -dwell powerlaw_cutoff -lamb 0.0033 -hs 0.27
-
-  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
-  a real system, positional anti-correlation may dissipate after a sufficiently long 
-  time lag, dependent on the solute being studied. Second, it is difficult to reliably
-  parameterize the Hurst parameter which is important for accurately describing the 
-  curvature of the solute MSDs.
-
-  This analysis also suggests that working with only half of the data we collected
-  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
-  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
-  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
-  sFLMcut), but still appear to systematically under-predict the mean. We may be
-  operating on the border of the minimum amount of data required to accurately 
-  parameterize the AD model. Longer simulations and more independent trajectories may
-  be necessary. Therefore, in the next section we will work with parameters fit to the
-  full equilibrated portion of the solute trajectories, doubling the data.
-
-%MRS6: My instinct is to only show the graphs of the full model, with validation graphs shown in the supporting.
-We can talk about this.
-We do what the focus to be on what we can learn physically.
-The discussion gets pretty repetitive.
-
-%MRS6: be a bit clearer about how the MD MSD error bounds are calculated.  That becomes important for determining how accurate the modeling is. .
-
-%  However, in the case of acetic acid, this may only happen because the 
-%  Hurst parameter is overestimated. It appears we are operating on the border of the
-%  minimum amount of data required to accurately parameterize the AD model. Longer
-%  simulations and more independent trajectories may be necessary. Therefore, in 
-%  the next section we will work with parameters fit to the full equilibrated portion
-%  of the solute trajectories, doubling the data.
-
-%  This brief analysis highlights some of the shortcomings of the AD model. So far, we have 
-%  shown that it does a reasonable job of approximating the magnitude of the MD-MSD
-%  after a 500 ns time lag, but the shape can sometimes be qualitatively wrong because of
-%  inaccurate Hurst parameters. In the case of acetic acid, a poorly measured $H$, but 
-%  accurate prediction of the magnitude of the MSD after 500 ns, may mask underlying 
-%  problems with the parameters of the hop length and dwell time distributions. Acetic
-%  acid has the lowest MSD of the solutes studied, therefore these issues may be resolved
-%  by longer simulations.
-
-  %BJC4: comment here about the length of time simulations need to be run in 
-  % order to get reliable data
-  % Or maybe a little later since acetic acid, although stationary
-  % comment on acetic acid's trajectory shape.
-
-  \subsubsection{Model predictions using all equilibrated data}\label{section:AD_all_data}
-
-  We obtain reasonable predictions of the MD simulated MSDs when we parameterize the AD 
-  model with all available data after the perceived equilibration time. Although we 
-  concluded that methanol and ethylene glycol trajectories are not yet stationary, we 
-  include them in all analysis going forward because it is still instructive. 
-  The MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
-  comparison in Figures~\ref{fig:anomalous_msds_1mode} and~\ref{fig:anomalous_msds_2mode}
-  respectively. The associated parameters are presented in Figures~\ref{fig:1mode_parameters}
-  and~\ref{fig:2mode_parameters}.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE.pdf}
-  \caption{Urea}\label{fig:1mode_msd_comparison_URE}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_GCL.pdf}
-  \caption{Ethylene Glycol}\label{fig:1mode_msd_comparison_GCL}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_MET.pdf}
-  \caption{Methanol}\label{fig:1mode_msd_comparison_MET}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH.pdf}
-  \caption{Acetic Acid}\label{fig:1mode_msd_comparison_ACH}
-  \end{subfigure}
-  \caption{In most cases, MSDs generated from realizations of our 1 mode anomalous
-  lie within or near the 1$\sigma$ confidence intervals of MD-generated data when using an
-  exponential cutoff on the dwell time distribution (sFBMcut and SFLMcut). When we
-  do not apply an exponential cut-off (sFBM and SFLM), MSDs are underpredicted. 
-  Drawing hops from a truncated L\'evy stable distribution yields MSDs similar to 
-  when hops are drawn from Gaussian disributions (sFLM and sFLMcut). In most 
-  cases, the MSDs are under-predicted at long timescales because the AD models
-  show pronounced curvature which the MD simulations lack.}\label{fig:anomalous_msds_1mode}
-  \end{figure}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE.pdf}
-  \caption{Urea}\label{fig:2mode_msd_comparison_URE}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_GCL.pdf}
-  \caption{Ethylene Glycol}\label{fig:2mode_msd_comparison_GCL}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_MET.pdf}
-  \caption{Methanol}\label{fig:2mode_msd_comparison_MET}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH.pdf}
-  \caption{Acetic Acid}\label{fig:2mode_msd_comparison_ACH}
-  \end{subfigure}
-  \caption{MSDs generated from realizations of our 2-mode anomalous diffusion model
-  predict the magnitude of the MSDs to a similar degree of accuracy as the 1 mode
-  model. Relative to the predictions of the 1 mode model the MSDs lack curvature because
-  the hop correlation structure is broken every time a transition between tails occurs.}\label{fig:anomalous_msds_2mode}
+  \includegraphics[width=\textwidth]{bothmode_msd_comparison_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:bothmode_msd_comparison_ACH}
+  \end{subfigure}
+  \caption{In most cases, MSDs generated from realizations of our 1 and 2 mode AD 
+  models lie within or near the 1$\sigma$ confidence intervals of MD-generated 
+  data. Drawing hops from a truncated L\'evy stable distribution (sFLMcut) yields
+  MSDs similar to  when hops are drawn from Gaussian distributions (sFBMcut). 
+  In most cases, the 1 mode simulated MSDs are under-predicted at long timescales
+  because they show pronounced curvature which the MD MSDs lack. The 2 mode predictions
+  show less curvature than the 1 mode MSDs because the hop correlation structure
+  is broken every time a transition between tails occurs.
+  }\label{fig:anomalous_msds}
   \end{figure}
@@
   \centering
-  \begin{subfigure}{0.475\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{2mode_AD_hops.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.475\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
@@
   \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{AD_mode_occupation.pdf}
+  \caption{}\label{fig:AD_mode_occupation}
+  \end{subfigure}
   \caption{
-  %MRS6: shouldnt the values be positive below the axis as well (if that can be done) I guess they are for b, but not for A.
-  %BJC6: yes, oversight, thanks.
   The two mode model parameterizes solute behavior in the pore and tails separately.
@@
   center, otherwise they are in the tails. (a) Generally, movement is much more restricted
-  in the tail region shown by lower $\sigma$ values (smaller hops) for the normal and L\'evy stable 
-  distributions. Values of $\alpha$ are significantly lower for urea and acetic acid meaning 
+  in the tail region, parameterized by lower $\sigma$ values (smaller hops) for the normal and L\'evy stable 
+  distributions. Values of $\alpha_h$ are significantly lower for urea and acetic acid meaning 
   there is a larger probability that they will take large hops. (b) Dwell times are longer in 
@@
   for both modes (shown in Figure~\ref{fig:hurst_barchart}) due to a low number of 
-  sufficiently long sequences of hops in each mode.}
-  \label{fig:2mode_parameters}
+  sufficiently long sequences of hops in each mode. (c) Solutes spend various amounts of 
+  time in the tail and pore region dependent on their size, shape and chemical functionality.
+  Methanol's small size favors occupation of the much larger accessible volume in the tails. 
+  Urea and acetic acid are fairly stable in both regions since they are small and hydrophilic.
+  Ethylene glycol has a slight preference for the pores likely because it is a larger molecule
+  with two hydrophilic hydroxyl groups.
+  }\label{fig:2mode_parameters}
   \end{figure}
@@
   After a 1000 ns time lag, the 1 and 2 mode AD models do a fairly good job of 
-  predicting the magnitude of the MD MSD curves when we use truncated power
-  laws to describe the dwell time distributions. In most cases, the sFBMcut
+  predicting the magnitude of the MD MSD curves.
+  % when we use truncated power
+  %laws to describe the dwell time distributions.
+  In most cases, the sFBMcut
   and sFLMcut models give very similar results probably because their $\alpha_h$
@@
   the predicted curves appears accurate relative to MD at short time lags.  
-  However, they to undershoot the MD MSD mean as the time lag increases. As 
-  discussed in the previous section, long time
-  positional anti-correlation may not exist in the MD system which results 
+  However, they undershoot the mean MD MSD as the time lag increases. As 
+  discussed in the previous section, long time positional anti-correlation, on
+  the order of hundreds of $ns$, may not exist in the MD system which results 
   in a shift from sub-linear to linear MSD behavior. Acetic acid exemplifies
-  this point. At first glance, acetic acid's predicted MSD (sFLMcut and sFBMcut)
-  appears to match the curvature of MD quite well, but closer examination reveals
-  that the MD MSD curve actually shifts from a sub-linear to a linear regime 
-  around 500 ns.
-
-  %MRS6: is it more or less physical that it has this behavior? 
-  The 2 mode models shows considerably less curvature at large time lags than
-  the 1 mode model because the implementation of the 2 mode model prevents long
-  timescale correlation. The width of the hop distribution changes every time
-  a switch between pores and tails occurs. We are unaware of an appropriate
-  technique which can correlate hops that come from different hop distributions, 
-  therefore every time a mode switch occurs, the correlation structure is 
-  broken. Solutes which switch between modes the least show the greatest
-  curvature. Methanol spends $> 90\%$ of its time in the tails, so mode transitions
-  are relatively rare and the predicted MSD has significant curvature. This artificially
-  solves the problem of long timescale correlation, however we do not recommend this
-  as it has no theoretical basis.
-
-  % In all but one case (two mode 
-  % ethylene glycol), MSD curves predicted by the sFLMcut model are higher than 
-  % those predicted by the sFBMcut model because of the heavy tails of the L\'evy 
-  % stable hop length distribution.
-
-%  Qualitatively, the curves with the highest final MSDs (ethylene glycol and 
-%  methanol) show more linear growth and their shapes are well captured by the
-%  sFLMcut and sFBMcut AD models. The MSD curve of urea bends slightly and 
-%  that of acetic acid has the most significant curvature. When the MD MSD 
-%  curves bend, the MSD curves predicted by the sFBMcut model tends to more 
-%  accurately portray their curvature since the sFLMcut model tends to become 
-%  linear faster.
-%  
-%  Acetic acid is a notable exception as no model accurately predicts its
-%  MSD or curvature. Both sFBMcut and sFLMcut significantly over-predict the final
-%  MSD while sFBM and sFLM significantly under-predict it. Once again, it 
-%  appears that the Hurst parameter may be over-estimated. However, the parameters
-%  of the hop and dwell distributions may be improved over those used to produce
-%  Figures~\ref{fig:1mode_msd_comparison_ACH_train_front} and
-%  \ref{fig:2mode_msd_comparison_ACH_train_front}. A lower value of $H$ would 
-%  increase the curvature and reduce the AD predicted MSD to values more consistent
-%  with acetic acid's MD MSD.
-
-%  Despite their deviations from the MD, the ranking of the magnitude of predicted
-%  MSDs remains the same as MD: ethylene glycol $\approx$ methanol $>$ urea $>$ acetic acid.
-%%  The discrepancies between MD and the predictions of the AD model may be resolved
-%%  by gathering longer and a greater quantity of solute trajectories
-%  Therefore, we can use the current parameters to understand solute dynamics.
+  this point. At first glance, acetic acid's predicted MSD appears to match the 
+  curvature of MD quite well, but closer examination reveals that the MD MSD 
+  curve actually shifts from a sub-linear to a linear regime around 500 ns.
+
+  The 2 mode models display curvature more consistent with MD but for non-physical
+  reasons. The width of the hop distribution changes every time a switch between
+  pores and tails occurs. We are unaware of an appropriate technique which can 
+  correlate hops that come from different hop distributions, therefore every 
+  time a mode switch occurs, the correlation structure is broken. Solutes that
+  switch between modes the least show predicted MSDs with the greatest curvature. 
+  Methanol spends $> 90\%$ of its time in the tails (see Figure~\ref{fig:AD_mode_occupation}),
+  so mode transitions are relatively rare and the predicted MSDs have significant 
+  curvature. This artificially solves the problem of long timescale correlation, 
+  however we do not recommend this as it has no theoretical basis.
 
@@
   limit of 0.5 indicate a lower degree of negative correlation between hops. All 
-  of these model parameters contribute to 
+  of these changes in physical behavior contribute to 
   %MRS6: increase in the MSD compared to what, be specific?
   %BJC6: made more specific
-  an overall increase in the predicted MSD and can be correlated to physical behavior 
-  that explains differences in the MD MSDs.
+  an overall increase in the predicted MSD.
+  % and can be correlated to physical behavior 
+  %that explains differences in the MD MSDs.
 
@@
   trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
-  relatively similar which is consistent with their similar MD MSDs. Methanol 
-  tends to stay trapped for less time and takes larger hops but the most substantial
-  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
-  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
-  it appears that our model under-predicts the methanol MSD curve relative
-  to other solutes. However, it remains plausible that methanol does have a low $H$ 
-  value because it spends the majority of its time outside the pore region where collisions
-  with tails are frequent. Urea has the third highest MSD which is primarily a consequence of
-  more frequent and longer dwell times, indicated by lower values of $\alpha$ and 
-  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
-  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
-  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
-  by an $\alpha$ value significantly lower than other solutes, but an intermediate 
-  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
-  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
-  (lower $\alpha_h$) than the other solutes.
+  relatively similar which is consistent with their similar MD MSDs. Relative to 
+  ethylene glycol, methanol tends to stay trapped for less time and takes larger hops
+  but the most substantial difference is with respect to their Hurst parameters.  
+  Methanol has the lowest $H$ of all the solutes studied because it spends the majority
+  of its time outside the pore region where collisions with tails are frequent.
+% BJC: made more to the point
+%  In fact, methanol has the lowest
+%  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
+%  it appears that our model under-predicts the methanol MSD curve relative
+%  to other solutes. However, it remains plausible that methanol does have a low $H$ 
+%  value because it spends the majority of its time outside the pore region where collisions
+%  with tails are frequent. 
+  Urea has the third highest MSD which is primarily a consequence of more frequent and
+  longer dwell times (lower $\alpha$ and $\lambda$). Urea's hop lengths ($\sigma$) and
+  correlation ($H$) are comparable to ethylene glycol and methanol. Acetic acid has the
+  smallest MSD among the solutes studied due to longer periods of entrapment and shorter
+  hops. Its trapping behavior is parameterized by an $\alpha$ value significantly lower
+  than other solutes, but an intermediate $\lambda$ value, suggesting it experiences 
+  many medium-length periods of entrapment. Its hops are smaller but are slightly 
+  compensated by a heavier tailed distribution (lower $\alpha_h$) than the other solutes.
 
@@
 
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{AD_mode_occupation.pdf}
-  \caption{Solutes spend various amounts of time in the tail and pore region dependent
-  on their size, shape and chemical functionality. Methanol's small size favors 
-  occupation of the much larger accessible volume in the tails. Urea and acetic acid
-  are fairly stable in both regions since they are small and hydrophilic. Ethylene 
-  glycol has a slight preference for the pores likely because it is a larger
-  molecule with two hydrophilic hydroxyl groups.}\label{fig:AD_mode_occupation}
-  \end{figure}
-
+  %BJC6: Could delete this paragraph or move an abridged version to conclusions
   Overall, the AD model does a reasonable job of predicting solute MSDs and its 
@@
 
-  %Solutes which achieve higher MSDs
-  %in a given amount of time appear to be more accurately parameterized.
-
-%  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
-%  of $\alpha$ for pure and truncated power law fits to the dwell time distributions of 
-%  urea, ethylene glycol and methanol are similar. The value of $\alpha$ for acetic
-%  acid is significantly lower than the rest of the solutes meaning it stays trapped 
-%  for long periods of time more frequently. The value of $\lambda$ is largest for
-%  methanol indicating that its longest dwell time is shorter than the longest dwell
-%  times of all other solutes. When hops are fit to a Gaussian, it is clear that acetic
-%  acid takes the smallest hops while methanol takes the largest. If we fit hops to a
-%  L\'{e}vy stable distribution, we observe a similar trend in $\sigma$ values, but 
-%  with varying weights on the distribution's tails. Acetic acid has the heaviest
-%  tails (lowest $\alpha_h$), meaning it is more likely to take large hops, while 
-%  ethylene glycol stays close to a Gaussian distribution (i.e. $\alpha_h$ near 2).
-%  The Hurst parameters indicate a moderate degree of anti-correlation between hops. 
-%  Surprisingly, methanol takes the most anti-correlated hops (lowest $H$). This is
-%  likely because methanol spends the largest fraction of its time within the pores. 
-%  It can still make large hops thanks to its small size, but tends to bounce around
-%  the tails.
-
-%  BJC4: urea and ethylene glycol only
-%  The parameters of the 1 mode model are similar between urea and ethylene glycol which 
-%  is not surprising considering their similar MD MSDs. Dwell times by 
-%  ethylene glycol are shorter as shown by its larger $\alpha$ and $\lambda$ values. Both
-%  solutes make similarly sized hops with hop distributions that are relatively close 
-%  to Gaussian (i.e. $\alpha_h$ near 2) when fit to a L\'evy stable distribution. Finally,
-%  both solutes exhibit a similar degree of correlation between hops with ethylene glycol
-%  exhibiting motion closer to Brownian.
-
-%  The difference in parameters of each mode of the 2 mode sFBM model offer additional
-%  mechanistic insight which the 1 mode model lacks. It is clear that solutes are 
-%  significantly slowed while they are in the tail region (mode 2) where long dwell times
-%  are more probable and hops are smaller (smaller $\alpha$). 
-% BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
-% The values of $\lambda$, however, do not 
-% appear to be directly correlated to mode. For example, $\lambda$ for ethylene glycol is
-% lower in the pores, meaning its longest dwell times in the pores are longer than its
-% longest dwell times in the tails. This may be a consequence of    
-%  Interestingly, $\alpha_h$ for urea and acetic acid in mode 2 is 1.50 meaning its 
-%  hop distribution is heavy tailed relative to ethylene glycol and methanol whose 
-%  $\alpha_h$ values are more consistent with a Gaussian distribution. Acetic acid and
-%  urea are structurally similar molecules, both planar with two heavy atoms attached to
-%  a carbonyl group. Their small size and rigid shape may allow them to slip through 
-%  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
-%  larger jumps to escape traps.
-
-%  BJC4: Urea and ethlyene glycol only
-%  The parameters of the 2 mode model are again similar between urea and ethylene glycol, 
-%  but the difference between parameters of each mode offer more detailed mechanistic
-%  insight than the 1 mode model. It is clear that solutes are significantly slowed while
-%  they are in the tail region where long dwell times are more probable (lower $\alpha$)
-%  and hops are smaller (smaller $\sigma$).  
-%  Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
-%  heavy tailed relative to ethylene glycol which has an $\alpha$ more consistent 
-%  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
-%  the tails, it still has an appreciable probability of making large hops. This could 
-%  be a consequence of urea's relatively small size and rigid shape compared to ethylene glycol.
-  %Ethylene glycol is a linear chain that can
-  %easily become entangled among the alkane tails while urea is planar with its four
-  %heavy atoms bonded to a single central atom.
-
-  %BJC3: Is it a bad idea to acknowledge that there is no experimental data? I can 
-  % spin this paragraph in a different way.
-  %MRS4: can one to training and validation?  Train on 1/2 the data, then see how well it fits the other half?
-  %MRS4: also, you need to be more specific about choosing for WHAT purpose.  Different purposes could imply different models.
-%  Choosing which model to use for long timescale projections is not entirely obvious
-%  without experimental data to compare with. For our comparisons to MD, using a 
-%  truncated power law distribution is an obvious choice. However, given that extremely
-%  long dwells are a rare event, it is possible that studying a much larger set of 
-%  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
-%  distributions, the generality of L\'evy stable distributions is powerful, but the
-%  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
-%  accuracy and computational tractability. Treating the dynamics as fractional 
-%  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is well below 2.
-
-%  \noindent We can use the model to project our simulations out to very long timescales.
-%  \begin{itemize}
-%    \item We can not definitively say which combination of distributions are best to use.
-%    \item Although the longest observed dwell times and hop lengths are less than
-%    the length of the simulated trajectories and box lengths respectively, it is still possible
-%    that that extremely long dwell times and hops are observed experimentally in rare but
-%    significant cases.
-%    \item We present long timescale projections using combinations of each distribution in the
-%    table below
-%  \end{itemize}
-
-  % BJC2: table of long timescale projections using combinations of dwell and hop distributions. 
-  %% TABLE %%
-
   \subsection{The Markov State-Dependent Dynamical Model}\label{section:msm_results}
 
-  %BJC4: added transitional paragraph
+  %BJC5: could remove this transitional paragraph
   The AD model is useful if one does not know exact transport mechanisms 
@@
 
-  % BJC4: I moved this discussion up. It used to be after I presented the parameters
+  %BJC6: added subsection title
+  \subsubsection{Solute state preferences}\label{section:state_preferences}
+
   Solute size and chemical functionality influence which states are visited most frequently.
@@
   independent of which region they are in.
-
-  % BJC5: moved to previous section  
-%   Urea and acetic acid spend slightly more than half of
-%  their time in the tails (56\% and 62\% of their time respectively) while ethylene
-%  glycol spends about 44\% of its time in the tails. Urea and acetic acid's compact
-%  and flat structure allows it to more easily partition into the tails while ethylene
-%  glycol prefers the pore region due to its two hydrophilic hydroxyl groups. Meanwhile
-%  methanol spends 91 \% of its time in the tails likely due to its small size.
 
@@
 
+  \subsubsection{Parameters of the MSDDM}\label{section:msddm_parameterization}
+
+  %BJC6: could delete this paragraph since described in methods
   To create an MSDDM for each solute, we determined the state sequence associated
@@
 
-%MRS6: even if the MSD is well predicted, if the trajectories look different, can it really be a useful model?
-I.e.
-is one getting the right answer for the wrong reasons?
-What does it mean if MSD's are good, but the dwell times are not great?
-  Qualitatively, realizations of the MSDDM are not consistent with MD solute
-  trajectories. Using the parameters shown in Figure~\ref{fig:msddm_parameters}
-  we generated realizations of the MSDDM and plotted a typical realization for each
-  solute in Figure~\ref{fig:msddm_eyetest}. Except in rare cases, the solutes do not make
-  large hops. There are two reasons for this behavior. First, the width of 
-  hop length distributions are much smaller than those of the AD model. Closer
-  examination of urea's MD trajectories shown in Figure~\ref{fig:solute_trajectories} 
-  reveal that hops tend to be an accumulation of a series of hops in the same direction.
-  All of the hops in the MSDDM are negatively correlated which prevents this from happening.
-  The second reason is a consequence of using a single hop length distribution 
-  for transitions. Many transitions occur between two trapped states where the 
-  transitional hops are actually very small. Our model ignores this physical 
-  restriction which can cause the solute to drift rather than stay trapped.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{msddm_realizations.pdf}
-  %MRS6: see above - right for wrong reasons?
-  \caption{Realizations of the MSDDM for each solute do not reproduce the hopping
-  and trapping behavior observed in our MD simulations. Except for a few large 
-  hops, the trajectories are qualitatively similar to what one might expect for
-  Brownian motion. Note that the length of the realizations are equal to the length
-  of the equlibrated portion of the MD trajectories for each solute.}\label{fig:msddm_eyetest}
-  \end{figure}
-
-  %Methanol's
-  %MSD is over-predicted at short timescales while acetic acid's entire MSD 
-  %curve is severely over-predicted.
+  \subsubsection{Application of the MSDDM}\label{section:msddm_application}
+
+% reordered this section to make the logic more clear
+
+  %Despite qualitative differences in trajectory realizations, 
+  The dynamics of urea, ethylene glycol and, to a lesser extent, methanol appear
+  to be well-captured by the MSDDM. We simulated 1000 MSDDM trajectory realizations
+  for each solute, as described in Section~\ref{method:MSMs}, then calculated their
+  MSDs (see Figure~\ref{fig:msddm_performance}). In most cases, the MSDDM predicts
+  the magnitude of the MD MSDs within their 1$\sigma$ confidence intervals. One 
+  could argue that the curves of ethylene glycol and urea are statistically 
+  indistinguishable. However, it's possible that they may diverge on longer 
+  timescales due to differences in their curvature. Similarly, methanol's MD MSD 
+  is nearly linear while the MSDDM prediction is curving downward implying that it
+  may underestimate the MSD on longer timescales.
+
+  The predicted MSD of acetic acid is severely over-estimated primarily due to
+  under-estimation of hop anti-correlation ($H$ too high) and an over-estimate of 
+  its hop lengths ($\sigma$ too high). As stated earlier, most of a solute's 
+  motion is due to displacements during state transitions. Acetic acid has a 
+  transitional Hurst parameter close to urea's and a transitional $\sigma$ value
+  that is higher than urea's. This suggests that the heavier tails of urea's transitional
+  hop distribution (greater $\alpha_h$ value) are in large part responsible for 
+  urea's higher predicted MSD. Although, note that acetic acid's predicted MSD
+  actually lies just within the lower bound of urea's MD MSD 1$\sigma$ 
+  confidence interval. There is also the strong possibility that the over-estimate is
+  a consequence of lumping together all of acetic acid's transitional hops into
+  a single correlated distribution.
 
@@
 
-  Despite qualitative differences in trajectory realizations, the dynamics of 
-  urea, ethylene glycol and, to a lesser extent, methanol appear to be well-captured
-  by the MSDDM. We simulated 1000 MSDDM trajectory realizations for each solute, as
-  described in Section~\ref{method:MSMs}, then calculated their MSDs (see 
-  Figure~\ref{fig:msddm_performance}). In most cases, the MSDDM predicts the magnitude of the MD MSDs 
-  within their 1$\sigma$ confidence intervals. One could argue that the curves
-  of ethylene glycol and urea are statistically indistinguishable. However, 
-  it's possible that they may diverge on longer timescales due to differences
-  in their curvature. Similarly, methanol's MD MSD is nearly linear while 
-  the MSDDM prediction is curving downward implying that it may underestimate
-  the MSD on longer timescales.
-
-  The predicted MSD of acetic acid is severely over-estimated most likely due
-  to poor parameterization. 
-  %MRS6: poor parameterization is vague.  Of which features?
-As stated earlier, most of a solute's motion is 
-  due to displacements during state transitions. Acetic acid has a transitional
-  Hurst parameter close to urea's and a transitional $\sigma$ value that 
-  is higher than urea's. This suggests that the heavier tails of urea's transitional
-  hop distribution (greater $\alpha_h$ value) are in large part responsible for 
-  urea's higher predicted MSD. Although, note that acetic acid's predicted MSD
-  actually lies just within the lower bound of Urea's MD MSD 1$\sigma$ 
-  confidence interval. There is also the strong possibility that the over-estimate is
-  a consequence of lumping together all of acetic acid's transitional hops into
-  a single correlated distribution.
-
-  The MSDDM suffers similar shortcomings to the AD model. First, curvature 
-  on long timescales due to positional anti-correlation may result in 
-  underestimates of the MSD at large time lags. As suggested earlier, truncating
-  the positional autocorrelation function may help solve this issue. Second, 
-  parameterization can be challenging. In addition to possibly poor estimates 
-  of the Hurst parameter, we made the simplifying assumption that we could lump
-  all transitional hops into a single distribution. While this appears to work
-  in most cases, it is the source of qualitative mismatches between MSDDM
-  realizations and MD simulation trajectories and it may be the source of the 
-  over-estimate of acetic acid's MSD.
-
-  The MSDDM offers mechanistic insight and, in 3 out of 4 cases, gives reasonable
-  predictions of solute MSDs. To successfully apply the model, one must know 
-  representative discrete states beforehand or apply some technique to identify
-  them. At the very least, we can used the MSDDM to obtain a detailed quantitative
-  picture of dynamics within each state in terms of the magnitude of their 
-  fluctuations and correlation with previous motion. If we have confidence in
-  their predictive ability, then we can project solute trajectories out to 
-  macroscopic timescales and estimate macroscopic observables such as solute 
-  flux and selectivity.
-
-%  Unfortunately correlation between adjacent same-state sequences is lost
-%  with our model which causes the MSDs to be significantly over-predicted. The MSDDM
-%  may be suitable for processes with rarer transitions between states. If we can 
-%  further reduce the state-space of our models, it may have better predictive success,
-%  but we lose mechanistic detail.
-
-% BJC5: following not true
-%  The MSDDM overestimates solute MSDs because correlation is lost every time a
-%  state switch occurs. Although correlation exists within each sequence, there
-%  is no memory of the previous state or state transition that can be built into
-%  the first emission of the most recent state. This implies that the first 
-%  value in a state sequence is a random draw from the underlying emission 
-%  distribution. Frequent transitions between states lead to an abundance of 
-%  short dwell times. It is difficult to accurately correlate short sequences so
-%  we are almost simulating uncorrelated draws from the emission distribution.
-%  In Figure~\ref{fig:T_sensitivity}, we demonstrate this effect by varying the
-%  transition matrix and simulating a simple 2-state model with parameters similar
-%  to those in Table~\ref{table:msddm_params} (we tabulated the parameters used 
-%  in Table~\ref{S-table:msddm_params} of the Supporting Information). We modified
-%  the probability transition matrix, $T$, in order to control the probability of 
-%  self-transitions (the diagonal elements of $T$). Larger self-transition 
-%  probabilities lead to longer dwell times in each state. We set the off-diagonal
-%  elements of $T$ to be equal values that make the rows of $T$ sum to unity when
-%  combined with the self-transition probabilities. As we increase the 
-%  self-transition probability, $T_{ii}$, the simulated MSD decreases. Consequently,
-%  longer dwell times in each state allow us to more accurately simulate the
-%  negative correlation that we observe in MD.
+%MRS6: even if the MSD is well predicted, if the trajectories look different, can it really be a useful model?
+I.e.
+is one getting the right answer for the wrong reasons?
+What does it mean if MSD's are good, but the dwell times are not great?
+  Despite relatively good predictions of the MD MSD, qualitative mismatch
+  between simulated MSDDM and MD trajectories suggest that the MSDDM may be 
+  getting the right answers for the wrong reasons. We plotted typical 
+  realizations of the MSDDM for each solute and compared them to MD in 
+  Figure~\ref{fig:msddm_eyetest}. There is little evidence of trapping behavior or
+  large hops. There are two reasons for this behavior. First, the width of 
+  hop length distributions are much smaller than those of the AD model. Closer
+  examination of the characteristic MD trajectories shown in Figure~\ref{fig:solute_trajectories} 
+  reveal that hops tend to be an accumulation of a series of hops in the same direction.
+  All of the hops in the MSDDM are negatively correlated which prevents this from happening.
+  The second reason is a consequence of using a single hop length distribution 
+  for transitions. Many transitions occur between two trapped states where the 
+  transitional hops are actually very small. Our model ignores this physical 
+  restriction which can cause the solute to drift rather than stay trapped.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{stacked_msddm_realizations_URE.pdf}
+  \caption{Urea}\label{fig:stacked_msddm_realizations_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{stacked_msddm_realizations_GCL.pdf}
+  \caption{Ethylene glycol}\label{fig:stacked_msddm_realizations_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{stacked_msddm_realizations_MET.pdf}
+  \caption{Methanol}\label{fig:stacked_msddm_realizations_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{stacked_msddm_realizations_ACH.pdf}
+  \caption{Acetic Acid}\label{fig:stacked_msddm_realizations_ACH}
+  \end{subfigure}
+  \caption{Realizations of the MSDDM for each solute (blue) do not reproduce 
+  the hopping and trapping behavior observed in our MD simulations (black). 
+  The trajectories are qualitatively similar to what one might expect for 
+  Brownian motion. 
+  %Note that 
+  %the length of the realizations are equal to the length of the equilibrated 
+  %portion of the MD trajectories for each solute.
+  }\label{fig:msddm_eyetest}
+  \end{figure}
+
+% BJC6: I removed these because I think it doesn't add much. Could add a bit 
+% more to the conclusions.
+%  The MSDDM suffers similar shortcomings to the AD model. First, curvature 
+%  on long timescales due to positional anti-correlation may result in 
+%  underestimates of the MSD at large time lags. As suggested earlier, truncating
+%  the positional autocorrelation function may help solve this issue. Second, 
+%  parameterization can be challenging. In addition to possibly poor estimates 
+%  of the Hurst parameter, we made the simplifying assumption that we could lump
+%  all transitional hops into a single distribution. While this appears to work
+%  in most cases, it is the source of qualitative mismatches between MSDDM
+%  realizations and MD simulation trajectories and it may be the source of the 
+%  over-estimate of acetic acid's MSD.
 %  
-%  \begin{figure}
-%  \centering
-%  \includegraphics[width=0.5\textwidth]{T_sensitivity.pdf}
-%  \caption{As we increase the self-transition probabilities ($T_{ii}$) of an MSDDM,
-%  the simulated MSD of the process decreases because the negative correlation structure
-%  of individual state sequences is simulated more accurately.}\label{fig:T_sensitivity}
-%  \end{figure}
+%  The MSDDM offers mechanistic insight and, in 3 out of 4 cases, gives reasonable
+%  predictions of solute MSDs. To successfully apply the model, one must know 
+%  representative discrete states beforehand or apply some technique to identify
+%  them. At the very least, we can used the MSDDM to obtain a detailed quantitative
+%  picture of dynamics within each state in terms of the magnitude of their 
+%  fluctuations and correlation with previous motion. If we have confidence in
+%  their predictive ability, then we can project solute trajectories out to 
+%  macroscopic timescales and estimate macroscopic observables such as solute 
+%  flux and selectivity.
 
@@
 
-  %MRS6: to what extent can be 'cut' models be the ones used, and the untruncated ones thrown out early in the paper to simplify the presentation. 
   We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
-  diffusion model and the MSDDM in order to demonstrate how one can use their realizations
-  in order to calculate the flux (see section~\ref{method:mfpt}) of solutes given model 
-  parameters extracted from MD simulations. The 1-mode sFBMcut model generates predictions
-  similar to the 1-mode sFLMcut model at a lower computational cost and is far more
-  accurate than sFBM and sFLM. We showed that the 2-mode AD model has a broken correlation
-  structure, so we do not consider it here.
-
-  %BJC4: not sure if the next couple paragraphs belong in methods 
-  %MRS5: this could potentially be in methods.  Alternatives can be discussed there.
-  %BJC5: I tried putting this in methods, but it feels weird without stating the
-  % empirical equation. And I'm avoiding stating the empirical model in the methods
-  % since it is informed by the data.
+  diffusion model and the MSDDM in order to demonstrate how one can use their 
+  realizations in order to calculate the flux (see section~\ref{method:mfpt}) 
+  of solutes given model parameters extracted from MD simulations. The 1-mode 
+  sFBMcut model generates predictions similar to the 1-mode sFLMcut model at 
+  a lower computational cost. We showed that the 2-mode AD model has a broken
+  correlation structure, so we do not consider it here.
+
   It is computationally infeasible to simulate trajectories long enough that they
@@
   of 1 day to simulate 10000 sFBMcut realizations of solutes traversing a 50 nm pore.
-  The computational requirements of the MSDDM are about 10 times longer. For both
-  models, the RAM requirements and performance scales greater than linearly and 
-  thus would take an infeasible amount of memory and time to simulate transport 
+  The computational requirements of the MSDDM can be greater than 10 times longer. 
+  For both models, the RAM requirements and performance scales greater than linearly
+  and thus would take an infeasible amount of memory and time to simulate transport 
   through a pore over 100 times longer.
@@
   \begin{equation}
-  J(L) = cL^{-\beta} 
+  J(L) = AL^{-\beta} 
   \label{eqn:flux_decay}
@@
   fluxes than the sFBMcut model. We fit the single particle solute flux versus pore
-  length, $L$, to a power law function of the form $cL^{-\beta}$ (dashed lines in (b)
+  length, $L$, to a power law function of the form $AL^{-\beta}$ (dashed lines in (b)
   and (c)). 
@@
 
+  %BJC6: could move this paragraph to supporting
   We determined that it is only necessary to simulate 1000 realizations of each model
@@
   flux, with minimal change to the mean flux values, using as few as 100 trajectory
-  realizations. 
-  %To be sure, 
-  For better precision, we recommend simulating at least 1000 realizations. 
+  realizations. For better precision, we recommend simulating at least 1000 realizations. 
   Since the computational cost of the MSDDM is greater than the AD model, we generated
@@
 
-  %The scaling of solute flux with pore length is a complicated function of hop and 
-  %dwell parameters, however, anti-correlation between solute hops appears to
-  %be the most significant influencing factor. 
   The scaling of solute flux with pore length is primarily influenced by anti-correlation
-  between solute hops. In Figure~\ref{fig:beta_hurst}, we show that $\beta$, as derived 
-  from the sFBMcut model, is inversely related to the Hurst parameter. This makes intuitive
-  sense since higher degrees of anti-correlation should slow the rate at which solutes
-  cross the membrane pore. $\beta$, as derived from the MSDDM, appears approximately 
-  constant but this is consistent with nearly invariant transitional Hurst parameters
-  (see Figure~\ref{fig:H_v_state}). However, Figure~\ref{fig:beta_hurst} does raise
-  the question as to why $\beta$ is so much lower than the sFBMcut model.
-
-  To understand the behavior of the MSDDM, we studied the $\beta$ parameter derived 
-  from variations on each model, visualized in Figure~\ref{fig:beta_parameters}. First, 
-  we removed anti-correlation between hops in the sFBMcut trajectory (set $H$=0.5). 
-  The $\beta$ parameter drops to values similar to the MSDDM. When we remove anti-correlation
-  \textit{and} dwell times between hops (set dwell times equal to 1), effectively simulating 
-  Brownian motion, we observe similar $\beta$ parameters. These two variations imply that,
-  in the AD models, the $\beta$ parameter is only a function of $H$ and not dependent on
-  dwell times ($\alpha$, $\lambda$) or hop lengths ($\sigma$). The MSDDM is fundamentally similar to 
-  the AD model in that one makes correlated draws from a hop distribution. Therefore,
-  we should expect the $\beta$ value of the MSDDM to be larger than that of Brownian 
-  motion.
+  between solute hops. In Figure~\ref{fig:beta}a, we show that $\beta$, as derived 
+  from the sFBMcut model, is inversely related to the Hurst parameter. 
+  % BJC6: I'm not sure this sentence adds anything
+  %This makes intuitive sense since higher degrees of anti-correlation should slow the rate at which solutes
+  %cross the membrane pore. 
+  $\beta$, as derived from the MSDDM, appears approximately constant which is 
+  consistent with nearly invariant transitional Hurst parameters (see 
+  Figure~\ref{fig:H_v_state}). However, Figure~\ref{fig:beta}a does raise
+  the question as to why $\beta$ is so much lower than the sFBMcut model. The MSDDM 
+  is fundamentally similar to the AD model in that one makes correlated draws 
+  from a hop distribution, therefore, we should expect the $\beta$ value of the
+  MSDDM to be larger than that of Brownian motion.
+
+  The length dependence of solute flux ($\beta$) for the MSDDM is under-estimated 
+  primarily due to innaccuracies in the correlation structure of very long FLM 
+  trajectories. To generate the curves in Figure~\ref{fig:flux_curves_msddm}, we 
+  needed to correlate 25--1000 times more hops than for the MSD predictions in 
+  Figure~\ref{fig:msddm_performance}. To understand the behavior of the MSDDM, we 
+  studied the $\beta$ parameter derived from variations on the SFBMcut model 
+  (see Figure~\ref{fig:beta}a), since we can generate exact realizations of FBM. 
+  First, we removed anti-correlation between hops in the sFBMcut trajectory (set
+  $H$=0.5). The $\beta$ parameter drops to values similar to the MSDDM. When we 
+  remove hop anti-correlation \textit{and} dwell times between hops (set dwell 
+  times equal to 1), effectively simulating Brownian motion, we observe similar 
+  $\beta$ parameters. These two variations imply that the $\beta$ parameter is 
+  only a function of $H$ and not dependent on dwell times ($\alpha$, $\lambda$) 
+  or hop lengths ($\sigma$). In Section~\ref{S-section:beta_estimates} of the 
+  Supporting Information we expand on this explanation and show that replacing 
+  inexact FLM realizations with exact FBM realizations recovers the pore length
+  dependence of solute flux.
+
   %Although the dwell times are
@@
 
-  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
-  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
-  Turning first to the model itself, we have designed it to ensure that the magnitude of the
-  hops in the series of transitions between states are anti-correlated from start to finish. 
-  This assumes that the transition correlation structure is unaffected by the
-  sub-trajectories between each state transition. Each time a state transition occurs, one
-  must initialize a new time series sub-trajectory with its own correlation structure. 
-  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
-  %in each state is relatively short making the accuracy of the correlation structure 
-  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
-  %$\sigma$ in trapped states. 
-  Since we add the transitional hop lengths to each end of
-  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
-  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
-  MSDDM to completely immobilize particles except when they transition between states. 
-  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
-  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
-  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
-  To generate the curves in Figure~\ref{fig:flux_curves_msddm}, we needed to correlate 
-  25--1000 times more hops than for the MSD predictions in Figure~\ref{fig:msddm_performance}. 
-  In short, it is computationally infeasible to use enough terms to accurately incorporate
-  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
-  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
-  fractional Brownian motion, for which we have an exact simulation method, in place of 
-  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
-  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
-  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
-  of FLM.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.43\textwidth}
-  \includegraphics[width=\textwidth]{beta_hurst.pdf}
-  \caption{}\label{fig:beta_hurst}
-  \end{subfigure}
-  \begin{subfigure}{0.52\textwidth}
-  \includegraphics[width=\textwidth]{beta_parameters.pdf}
-  \caption{}\label{fig:beta_parameters}
-  \end{subfigure}
-  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
-  %MRS6: should try to lead with what the overall results/conclusions are.
+%  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
+%  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
+%  Turning first to the model itself, we have designed it to ensure that the magnitude of the
+%  hops in the series of transitions between states are anti-correlated from start to finish. 
+%  This assumes that the transition correlation structure is unaffected by the
+%  sub-trajectories between each state transition. Each time a state transition occurs, one
+%  must initialize a new time series sub-trajectory with its own correlation structure. 
+%  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
+%  %in each state is relatively short making the accuracy of the correlation structure 
+%  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
+%  %$\sigma$ in trapped states. 
+%  Since we add the transitional hop lengths to each end of
+%  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
+%  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
+%  MSDDM to completely immobilize particles except when they transition between states. 
+%  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
+%  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
+%  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
+%  To generate the curves in Figure~\ref{fig:flux_curves_msddm}, we needed to correlate 
+%  25--1000 times more hops than for the MSD predictions in Figure~\ref{fig:msddm_performance}. 
+%  In short, it is computationally infeasible to use enough terms to accurately incorporate
+%  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
+%  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
+%  fractional Brownian motion, for which we have an exact simulation method, in place of 
+%  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
+%  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
+%  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
+%  of FLM.
+
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.43\textwidth}
+%  \includegraphics[width=\textwidth]{beta_hurst.pdf}
+%  \caption{}\label{fig:beta_hurst}
+%  \end{subfigure}
+%  \begin{subfigure}{0.52\textwidth}
+%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
+%  \caption{}\label{fig:beta_parameters}
+%  \end{subfigure}
+%  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
+%  %MRS6: should try to lead with what the overall results/conclusions are.
 What does it mean that parameters are larger or smaller?
@@
 Should it be in supportinig?
-  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
-  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
-  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
-  sub-trajectories between state transitions decorrelate transitional hops and because
-  our FLM simulation procedure does not accurately correlate hops after long time lags. 
-  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
-  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
-  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
-  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
-  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
-  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
-  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
+%  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
+%  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
+%  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
+%  sub-trajectories between state transitions decorrelate transitional hops and because
+%  our FLM simulation procedure does not accurately correlate hops after long time lags. 
+%  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
+%  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
+%  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
+%  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
+%  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
+%  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
+%  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
+%  \end{figure}
+
+  %BJC6: TODO: add (a), (b), (c)
+  \begin{figure}
+  \centering
+  \begin{subfigure}{\textwidth}
+  \includegraphics[width=\textwidth]{hurst_beta_variations.pdf}
+  \caption*{}\label{fig:beta_hurst}
+  \end{subfigure}
+  \begin{subfigure}{0.42\textwidth}
+  \vspace{-2em}
+  % use c_parameters2.py
+  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
+  \caption*{}\label{fig:c_parameters}
+  \end{subfigure}
+  \begin{subfigure}{0.53\textwidth}
+  \vspace{-2em}
+  \vspace{0.5em}
+  \includegraphics[width=\textwidth]{c_influence.pdf}
+  \caption*{}\label{fig:c_influence}
+  \end{subfigure}
+  \caption{(top) Increased anti-correlation between hops (decreased $H$) appears to 
+  increase the length-dependence of solute flux (higher $\beta$) for the sFBMcut model.
+  The length dependence of the MSDDM model is much weaker because sub-trajectories 
+  between state transitions decorrelate transitional hops and because our FLM 
+  simulation procedure does not accurately correlate hops after long time lags. 
+  We support this claim by removing hop correlation from the sFBMcut model which
+  results in a drop in the $\beta$ value close to MSDDM. These values of $\beta$ are
+  consistent with Brownian motion (no hop correlation and unit-length dwell times).
+  (bottom left) As solute flux increases, the scaling of the flux curves, $c$, increases 
+  (compare ranking with Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm}).
+  The $A$ parameters of the MSDDM are smaller than the sFBMcut AD model because the AD
+  model must compensate for its strong length dependence (higher $\beta$). 
+  (bottom right) Physical processes which increase the rate of solute displacement 
+  result in larger values of $A$. To test the dependence of $A$ on $\alpha$, $\sigma$, 
+  $H$ and $\lambda$, we chose a single set of parameters, representative of solutes
+  parameterized by the sFBMcut AD model, and generated realizations of the
+  model by each parameter independently about the same base parameter set. 
+  %Therefore, the middle bars for these four 4 parameters are 
+  %generated from the same set of parameters. 
+  Decreased dwell times (increased $\alpha$), increased hop lengths (increased 
+  $\sigma$), and a lower cut-off to the dwell time distribution (increased $\lambda$)
+  lead to increases in $A$. 
+  %$c$ responds linearly to increases in $\sigma$ and $\lambda$
+  and non-linearly to $\alpha$.
+  The data suggests that the $A$ parameters do not depend on hop anti-correlation ($H$).
+  To test $\alpha_h$, we used the set of parameters defining the MSDDM of Urea (since 
+  sFBMcut does not use a L\'evy distribution) and varied the $\alpha_h$ parameter of 
+  the transitional hops. As $\alpha_h$ increases, $A$ increases slightly since the 
+  density of the L\'evy stable PDF is shifted away from rare hops and broadened at 
+  its center. We expect similar dependence of $A$ on $\sigma$ and $H$ of the MSDDM.
+  }\label{fig:beta}
   \end{figure}
 
-  %MRS6: can this be made a physical thesis instead of a mathematical one?
-  The values of $c$ are directly related to the magnitude of solute flux and, where
-  applicable, are functions of $\sigma$, $\alpha$, $\lambda$ and $\alpha_h$. 
-  In Figure~\ref{fig:c_parameters}, we plot the $c$ values measured
-  for each solute with each model from lowest to highest. In general, $c$ values generated
-  by the MSDDM model are smaller than the those generated by the sFBMcut AD model 
-  because the AD model has to compensate for high $\beta$ values. Comparison 
-  of Figure~\ref{fig:c_parameters} with Figures~\ref{fig:flux_curves_ad} 
-  and~\ref{fig:flux_curves_msddm} reveals that the ranking of the $c$ parameters is
-  consistent with the ranking of solute flux. Therefore, it is reasonable to hypothesize
-  that any parameter which acts to modify the rate at which solutes move through the
-  membrane pores will affect $c$ for various physical reasons. In 
-  Figure~\ref{fig:c_influence} we demonstrate that decreased dwell times
-  (increased $\alpha$), increased hop lengths (increased $\sigma$), cutting off the
-  dwell time distribution at shorter times (increased $\lambda$) and decreased tail 
-  weights of the hop length distribution (increased $\alpha_h$) independently lead to
-  an increase in $c$. Figure~\ref{fig:c_influence} also suggests that $c$ is not dependent on hop
-  anti-correlation ($H$).
+  Parameters represented by physical processes which act to modify the rate at 
+  which solutes move through the membrane pores will affect the scaling pre-factor
+  of the solute flux curves ($A$). Comparison of Figure~\ref{fig:beta}b with 
+  Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm} reveals that
+  the ranking of the $A$ parameters is consistent with the ranking of solute 
+  flux. In general, $A$ values generated by the MSDDM model are smaller than the
+  those generated by the sFBMcut AD model because the AD model has to compensate
+  for high $\beta$ values. In Figure~\ref{fig:beta}c we demonstrate that 
+  decreasing dwell times (increasing $\alpha$), increasing hop lengths (increasing 
+  $\sigma$), cutting off the dwell time distribution at shorter times (increasing
+  $\lambda$) and increasing tail weights of the hop length distribution (decreasing
+  $\alpha_h$) independently lead to an increase in $A$. Figure~\ref{fig:beta}c
+  also suggests that $A$ is not dependent on hop anti-correlation ($H$).
+
+%  The values of $c$ are directly related to the magnitude of solute flux and, where
+%  applicable, are functions of $\sigma$, $\alpha$, $\lambda$ and $\alpha_h$. 
+%  In Figure~\ref{fig:beta}, we plot the $c$ values measured
+%  for each solute with each model from lowest to highest. In general, $c$ values generated
+%  by the MSDDM model are smaller than the those generated by the sFBMcut AD model 
+%  because the AD model has to compensate for high $\beta$ values. 
+%  Comparison 
+%  of Figure~\ref{fig:c_parameters} with Figures~\ref{fig:flux_curves_ad} 
+%  and~\ref{fig:flux_curves_msddm} reveals that the ranking of the $c$ parameters is
+%  consistent with the ranking of solute flux. 
+%  Therefore, it is reasonable to hypothesize
+%  that any parameter which acts to modify the rate at which solutes move through the
+%  membrane pores will affect $c$ for various physical reasons. 
+%  In 
+%  Figure~\ref{fig:c_influence} we demonstrate that decreased dwell times
+%  (increased $\alpha$), increased hop lengths (increased $\sigma$), cutting off the
+%  dwell time distribution at shorter times (increased $\lambda$) and decreased tail 
+%  weights of the hop length distribution (increased $\alpha_h$) independently lead to
+%  an increase in $c$. Figure~\ref{fig:c_influence} also suggests that $c$ is not dependent on hop
+%  anti-correlation ($H$).
 
@@
 
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.42\textwidth}
-  % use c_parameters2.py
-  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
-  \caption{}\label{fig:c_parameters}
-  \end{subfigure}
-  \begin{subfigure}{0.53\textwidth}
-  \vspace{0.5em}
-  \includegraphics[width=\textwidth]{c_influence.pdf}
-  \caption{}\label{fig:c_influence}
-  \end{subfigure}
-  %BJC5: waiting on simulations for alpha_h
-  \caption{(a) The $c$ parameter increases with solute flux (compare ranking with
-  Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm}). The $c$ parameters
-  of the MSDDM are smaller than the sFBMcut AD model because the AD model must
-  compensate for its strong length dependence (higher $\beta$). (b) Changes to parameters
-  which increase the rate of solute displacement result in larger values of $c$. 
-  To test the dependence of $c$ on $\alpha$, $\sigma$, $H$ and $\lambda$, we chose a 
-  single set of parameters, representative of solutes parameterized by the sFBMcut AD model,
-  and generated realizations of the model by varying each parameter independently about the
-  same base parameter set. Therefore, the middle bars for these four 4 parameters are 
-  generated from the same set of parameters. Decreased dwell times (increased $\alpha$),
-  increased hop lengths (increased $\sigma$), and a lower cut-off to the dwell time
-  distribution (increased $\lambda$) lead to increases in $c$. $c$ responds linearly
-  to increases in $\sigma$ and $\lambda$ and non-linearly to $\alpha$. The data 
-  suggests that the $c$ parameters do not depend on hop anti-correlation ($H$). To test 
-  $\alpha_h$, we used the set of parameters defining the MSDDM of Urea (since sFBMcut does
-  not use a L\'evy distribution) and varied the $\alpha_h$ parameter of the transitional
-  hops. As $\alpha_h$ increases, $c$ increases slightly since the density of the L\'evy
-  stable PDF is shifted away from rare hops and broadened at its center.
-  We expect similar dependence of $c$ on $\sigma$ and $H$ of the MSDDM.}\label{fig:c}
-  \end{figure}
-
 %  \begin{figure}
 %  \centering
-%  % bar charts
-%%  \begin{subfigure}{0.45\textwidth}
-%%  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
-%%  \end{subfigure}
-%%  \begin{subfigure}{0.45\textwidth}
-%%  \includegraphics[width=\textwidth]{beta_parameter_comparison.pdf}
-%%  \end{subfigure}
-%  \includegraphics[width=0.5\textwidth]{beta_c_parameter_comparison.pdf}
-%  \caption{}\label{fig:flux_parameters}
+%  \begin{subfigure}{0.42\textwidth}
+%  % use c_parameters2.py
+%  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
+%  \caption{}\label{fig:c_parameters}
+%  \end{subfigure}
+%  \begin{subfigure}{0.53\textwidth}
+%  \vspace{0.5em}
+%  \includegraphics[width=\textwidth]{c_influence.pdf}
+%  \caption{}\label{fig:c_influence}
+%  \end{subfigure}
+%  %BJC5: waiting on simulations for alpha_h
+%  \caption{(a) The $c$ parameter increases with solute flux (compare ranking with
+%  Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm}). The $c$ parameters
+%  of the MSDDM are smaller than the sFBMcut AD model because the AD model must
+%  compensate for its strong length dependence (higher $\beta$). (b) Changes to parameters
+%  which increase the rate of solute displacement result in larger values of $c$. 
+%  To test the dependence of $c$ on $\alpha$, $\sigma$, $H$ and $\lambda$, we chose a 
+%  single set of parameters, representative of solutes parameterized by the sFBMcut AD model,
+%  and generated realizations of the model by varying each parameter independently about the
+%  same base parameter set. Therefore, the middle bars for these four 4 parameters are 
+%  generated from the same set of parameters. Decreased dwell times (increased $\alpha$),
+%  increased hop lengths (increased $\sigma$), and a lower cut-off to the dwell time
+%  distribution (increased $\lambda$) lead to increases in $c$. $c$ responds linearly
+%  to increases in $\sigma$ and $\lambda$ and non-linearly to $\alpha$. The data 
+%  suggests that the $c$ parameters do not depend on hop anti-correlation ($H$). To test 
+%  $\alpha_h$, we used the set of parameters defining the MSDDM of Urea (since sFBMcut does
+%  not use a L\'evy distribution) and varied the $\alpha_h$ parameter of the transitional
+%  hops. As $\alpha_h$ increases, $c$ increases slightly since the density of the L\'evy
+%  stable PDF is shifted away from rare hops and broadened at its center.
+%  We expect similar dependence of $c$ on $\sigma$ and $H$ of the MSDDM.}\label{fig:c}
 %  \end{figure}
-
-  %MRS5: probably the figure showing beta \sim 2 can be in supporting
-  %information, and you just state the result here.
-  %MRS: can you put a physical thesis here, not just a mathematical one?  Why is this change in parameters important to flux? 
-%  The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
-%  solute MSD while the value of the growth exponent, $\beta$, is inversely 
-%  related to the Hurst parameter, $H$ (see Figure~\ref{fig:flux_parameters}).
-%  In Figure~\ref{fig:flux_curves_brownian}, we removed the correlation 
-%  structure (set $H$=0.5) from AD trajectory realizations so that all hops 
-%  were uncorrelated. Regardless of the parameters of the dwell time distribution,
-%  the growth exponent is always about 2, the same value that we observe for 
-%  Brownian motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the 
-%  Supporting Information).
-
-% BJC: following is wrong
-%  Dwell times between hops have a significant effect on the length dependence
-%  of solute flux. The values of $\beta$ fit to realizations of the sFBMcut AD
-%  model are significantly higher than the MSDDM. As evident by comparison of 
-%  Figures~\ref{fig:msddm_eyetest} and~\ref{fig:ad_eyetest}, realizations of the
-%  AD model exhibit much longer and more frequent periods of immobility. If we
-%  generate realizations of the sFBMcut model without trapping (dwell times are
-%  all 1 time step), the value of $\beta$ drops to 2 in all cases. In fact, we
-%  observe the same value of $\beta$ for Brownian motion (see Figure blah of the 
-%  Supporting Information) which implies that the Hurst parameter has no effect
-%  on the length dependence of flux.
-%  
-%  Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
-%  highlights that anti-correlation between hops plays a major role in solute flux.
-%  With a pore length of 50 nm, the flux of the fasted moving solute, ethylene glycol is 
-%  c.a. 5 times lower with versus without anti-correlated hops. The flux of the slowest
-%  moving solute, acetic acid, is about 16 times lower by the same comparison. This 
-%  difference will only grow with increasing pore length. Note also that the ranking
-%  of solute fluxes changes. Methanol jumps from the second lowest to the highest
-%  flux when we remove hop correlation. The high degree of anti-correlation among
-%  hops made by methanol outweighs its relatively wide hop length distribution.
-
-%MRS: can you connect directly to $\beta$ and $c$ here?  Important to
-%make connections between macroscopic parameters and the molecular
-%reason for them whenever possible.  Can combine with other paragraphs that talk mainly about c and beta.
-
-%   In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
-%  with pore length. We fit a curve of the form  to the curves in order
-%  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
-%  to the solute MSDs which is consistent with longer passage times for solutes that
-%  progress through the pores more slowly.
 
@@
   \begin{equation}
-  S_{ij}(L) = \bigg(\frac{c_i}{c_j}\bigg)L^{(\beta_i - \beta_j)}
+  S_{ij}(L) = \bigg(\frac{A_i}{A_j}\bigg)L^{(\beta_i - \beta_j)}
   \label{eqn:selectivity_ratio}
@@
 
-  %MRS5: figure seem to show that the selectivity plateaus more or less, so thin coatings enough. 
   In Figure~\ref{fig:selectivity}, we plot Equation~\ref{eqn:selectivity_ratio} for pore
   lengths ranging from those studied in Figure~\ref{fig:flux_curves} to macroscopic-length
-  pores. Greater differences in $\beta$ values leads to selectivities that are stronger 
-  functions of pore length. For $(c_i / c_j)=1$, LLC membranes will be more selective
-  towards passage of solutes with lower $\beta$ values versus those with high $\beta$ values.
-  When $\beta$ values are equal, as is the case for uncorrelated motion, selectivity only
-  depends on the pre-factors, $c$. In most cases, the length dependence of selectivity 
+  pores. 
+  %Greater differences in $\beta$ values leads to selectivities that are stronger 
+  %functions of pore length. 
+  For $(A_i / A_j)=1$, LLC membranes will be more selective towards passage of solutes 
+  with less anti-correlated hopping behavior (lower $\beta$). 
+  %versus those with high $\beta$ values.
+  For the same degree of hop anti-correlation, 
+  %When $\beta$ values are equal, 
+  as is the case for uncorrelated motion, selectivity only
+  depends on the pre-factors, $A$. In most cases, the length dependence of selectivity 
   plateaus quickly which implies that a coating of LLC membrane with a thickness on the 
   order of those already made experimentally should be sufficiently optimal.
-  %MRS5?
-can you remind people of the physical source (in terms of dwell times, hop lengths) of the differences in beta and c?
-Want to try to stablish the connection between particle dynamic behavior and selectivity.
 
@@
 
-  However, we may gain the most by using the two models in tandem. In both cases,  
-  the data suggests that this particular LLC membrane might be most useful for 
+  We may gain the most by using the two models in tandem. In both cases, the 
+  data suggests that this particular LLC membrane might be most useful for 
   selectively separating ethylene glycol from acetic acid. Ethylene glycol
@@
 
-%  Out of the solutes studied, the data suggests that this particular LLC membrane 
-%  %MRS5: would is a bit strong given the number of limitations.
-%  %would 
-%  might
-%  be most useful for selectively separating ethylene glycol from methanol and 
-%  acetic acid. 
-%  %It also shows reasonable selectivity of Urea over acetic acid.  
-%  Ethylene glycol has the highest $c$ value and the lowest $\beta$ value. The high
-%  value of $c$ itself greatly enhances its selective passage. Even more importantly,
-%  the relatively large difference between its $\beta$ value and those of methanol 
-%  and acetic acid give rise to a strong pore length dependence. The selectivity is
-%  enhanced as the pore length increases at the cost of lower solute flux, a 
-%  phenomenon ubiquitous in polymer separations membranes.~\cite{geise_water_2011}
-
-%  BJC4: Uncomment to see MFPT curves
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.325\textwidth}
-%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
-%  \caption{Correlated Hops}\label{fig:mfpt_curves_regular}
-%  \end{subfigure}
-%  \begin{subfigure}{0.325\textwidth}
-%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
-%  \caption{Uncorrelated Hops}\label{fig:mfpt_curves_brownian}
-%  \end{subfigure}
-%  \begin{subfigure}{0.325\textwidth}
-%  \includegraphics[width=\textwidth]{frac_pore.pdf}  % This figure might fit in earlier
-%  \caption{}\label{fig:frac_pore}
-%  \end{subfigure}
-%  \caption{(a) We fit the MFPT versus pore length to a function of the form $cL^{\alpha}$. 
-%  The MFPT grows super-linearly with increasing pore length. Solutes with lower MSDs have
-%  higher MFPTs. (b) If we remove correlation between hops, the MFPTs reduce significantly
-%  and the growth exponent stays constant at 2 for all solutes independent of dwell
-%  distribution parameters. Higher degrees of anti-correlation (lower $H$) lead to higher
-%  growth exponents. (c) Solutes that spend a large fraction of their time in the tails tend
-%  to have larger Hurst parameters.}\label{fig:mfpt_curves}
-%  \end{figure}
-
-%  In Figure~\ref{fig:frac_pore}, we show that solutes which spend more time in the tails
-%  tend to have lower Hurst parameters. The densely packed, viscoelastic alkane chains 
-%  bounce solutes between them, severely limiting their mobility. Designing LLC membranes
-%  that can control or prevent the partition of solutes into the tails may offer the highest
-%  returns on membrane performance.
-
-  %BJC: can make design suggestions by trying to decrease anticorrelation by x
-
-%  In this section, we use our most promising models to predict solute flux 
-%  through a theoretical 50 nm channel. For our comparisons to MD, using a truncated
-%  power law distribution is an obvious choice. However, given that extremely
-%  long dwells are a rare event, it is possible that studying a much larger set of 
-%  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
-%  distributions, the generality of L\'evy stable distributions is powerful, but the
-%  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
-%  accuracy and computational tractability. Treating the dynamics as fractional 
-%  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is 
-%  well below 2.
-%  
-%  Choosing which model to use for long timescale projections is not entirely obvious
-%  without experimental data to compare with.
-
-%  We projected the long timescale behavior using this model.
-
   \section{Conclusions}
@@
   offer important mechanistic insight on the molecular details of transport.
-  Subordinated fractional Brownian and L\'evy motion have a 
-  %nice 
-  strong theoretical 
+  Subordinated fractional Brownian and L\'evy motion have a strong theoretical 
   foundation in the anomalous diffusion literature. Our single mode model
@@
 
-  %MRS6: right answer, wrong reason for MSD match issue?
-  All of the models we tested have moderate success reproducing the MSDs of
-  solute trajectories generated by MD simulations. In almost all cases, large 
-  portions of the MSDs predicted by our models fall close to or within the 1$\sigma$
-  confidence intervals of MD. Aside from inaccuracies in parameter estimates,
-  the most significant shortcoming of all of our models is their ability to 
-  accurately portray the curvature of the MSD curves. The MD MSD curves tend to 
-  become linear on long timescales, but the MSD curves generated by our models
-  have persistent curvature that causes them to under-predict the MSD on very
-  long timescales. This is a consequence of the correlation structure associated
-  with fractional motion. In the future, we could address this by 
-  implementing a truncation to the positional autocorrelation function.
+  In their current state, one should use the predictions of our models with caution.
+  Although large portions of the MSDs predicted by our models fall close to or 
+  within the 1$\sigma$ confidence intervals of MD, it is not always for physically
+  accurate reasons. Qualitatively, MSDDM trajectories do not display the same hopping
+  and trapping behavior shown by MD trajectories. Frequent transitions drawn from a
+  single, relatively broad transition emission distribution prevent long periods of
+  immobility. The best solution to this would be to have individual emission distributions
+  for each type of transition, but this would require orders of magnitude more data. 
+  AD model realizations show appropriate qualitative behavior, but the persistent 
+  curvature of the computed MSD curves, due to the correlation structure of fractional 
+  motion, under-estimate the MD MSD curves which appear to be trending towards linear
+  on $\mu$s timescales. In the future, we could address this by implementing a truncation
+  to the positional auto-correlation function.
 
@@
   primarily due to the inexact method that we use to correlate hops of the 
-  fractional L\'evy motion process. When we replace FLM with FBM in the 
-  MSDDM algorithm, we observe a flux decay more consistent with that predicted
-  by the AD model. Finally, we used the ratio of solute fluxes in order to
-  calculate selectivity. Due differences in hop anti-correlation, we observe
-  a length dependent selectivity. However, this length dependence mostly
-  plateaus at length scales that can be synthesized experimentally. The data
-  suggests that this particular membrane may be useful for separating
-  ethylene glycol and acetic acid.
+  fractional L\'evy motion process. 
+  %When we replace FLM with FBM in the 
+  %MSDDM algorithm, we observe a flux decay more consistent with that predicted
+  %by the AD model. 
+  We used the ratio of solute fluxes generated from each model in order to 
+  calculate selectivity. Due to differences in hop anti-correlation, we observe 
+  a length dependent selectivity. This length dependence may dissipate
+  once we gain a more complete understanding of the hop correlation structure. 
+  If the length dependence of a properly correlated model always converges to 
+  $\beta$=2, it will greatly influence the prediction of selectivity on 
+  macroscopic length scales.
+%  However, this length dependence mostly plateaus at length scales that can be
+%  synthesized experimentally. The data suggests that this particular membrane 
+%  may be useful for separating ethylene glycol and acetic acid.
 
   % BJC5: I'm not sure if this paragraph belongs here. Or if it should go at end
-  % of previous section. Or just eliminate. What do you think?  
-  Of course, our approach to modeling LLC membrane selectivity neglects a number
-  of factors that influence real-world aqueous membrane separations. The most 
-  glaring is that we neglected convective flux which should work to increase 
-  overall solute flux and lower selectivity (see Equation ~\ref{eqn:solute_flux}).
-  Defects in the pore structure will have a strong influence on solute flux which
-  may exacerbate the length dependence of flux. Even in a perfectly structured 
-  membrane, the barrier to pore entry from the bulk solution will have its own 
-  influence on experimentally observed selectivities. This energetic barrier can 
-  be made even worse by foulants deposited on the membrane's surface. Therefore,
-  our predictions should be primarily used to identify the most promising types
-  of selective separations for an H\textsubscript{II} LLC membrane made from a 
-  specific monomer.
-
-  Our mathematical models help us think about how to design LLC monomers for 
-  solute-specific separations by forcing us to think in terms of controlling 
-  solute trapping. The anomalous diffusion model is quite flexible because it
-  does not require knowledge of specific trapping mechanisms. Screening a set
-  of solutes and applying the anomalous diffusion model can help uncover
-  trapping mechanisms by forcing the scientist to identify features common 
-  to solutes with long or short hop lengths and dwell times. The MSDDM is a 
-  powerful way to characterize explicit trapping mechanisms. It clearly
-  partitions a trajectory into discrete mechanisms and quantifies their
+  % of previous section. Or just eliminate. What do you think?  \
+  % BJC6: took out for now since I was questioning it. Can add back if reviewers ask about these considerations.
+%  Of course, our approach to modeling LLC membrane selectivity neglects a number
+%  of factors that influence real-world aqueous membrane separations. The most 
+%  glaring is that we neglected convective flux which should work to increase 
+%  overall solute flux and lower selectivity (see Equation ~\ref{eqn:solute_flux}).
+%  Defects in the pore structure will have a strong influence on solute flux which
+%  may exacerbate the length dependence of flux. Even in a perfectly structured 
+%  membrane, the barrier to pore entry from the bulk solution will have its own 
+%  influence on experimentally observed selectivities. This energetic barrier can 
+%  be made even worse by foulants deposited on the membrane's surface. Therefore,
+%  our predictions should be primarily used to identify the most promising types
+%  of selective separations for an H\textsubscript{II} LLC membrane made from a 
+%  specific monomer.
+
+  Despite their shortcomings, our mathematical models help us think about how 
+  to design LLC monomers for solute-specific separations by forcing us to think
+  in terms of controlling solute trapping. The anomalous diffusion model is 
+  quite flexible because it does not require knowledge of specific trapping 
+  mechanisms. Screening a set of solutes and applying the anomalous diffusion 
+  model can help uncover trapping mechanisms by forcing the scientist to 
+  identify features common to solutes with long or short hop lengths and dwell
+  times. The MSDDM is a powerful way to characterize explicit trapping mechanisms.
+  It clearly partitions a trajectory into discrete mechanisms and quantifies their
   relative dominance in the real system. For example, it is clear that 
@@
   complex separation problems.
-
-%  Properly parameterizing
-%  and simulating the correlation structure of the time series is very important. 
-%  Based on physical intuition, we assumed the correlation to be a consequence of 
-%  a fractional process however, autoregressive techniques may offer a more flexible
-%  approach.
-% Both models describe the trapping mechanism in
-%  different ways. The anomalous diffusion model does not consider mechanisms but
-%  insight into the length of entrapment
-%  
-%  The anomalous diffusion gives clues to the type 
-%  of functionality that leads to long dwell times. It is readily apparent that solute 
-%  
-%  One must consider how to control them and 
-%  a solute's preference towards the pore or tail region. 
-%  They can dissect solute movement down to their 
-%  individual positional fluctuations and give information about the influence 
-%  of the surrounding chemical environment. 
-%
-%  
-%  Combined with qualitative studies of solute transport to aid in model construction,
-%  our stochastic modeling framework can be used to quantitatively dissect the dynamic
-%  behavior of solutes in LLC membranes. Our work demonstrates that when designing a membrane for a 
-%  specific separation, one must consider the types of trapping mechanisms that 
-%  may play a role in transport, how solutes partition in the membrane,
 
@@
 
-  \clearpage
-
   %MRS6: look over and make bibliography consistent (i.e. no months, consistent journal abbreviations)
@@
   \bibliography{stochastic_transport}
-
-  \newpage
 

### 2020-01-12 LLC_Membranes/analysis/markov_state_dependent_dynamics.py

@@ -928,7 +928,7 @@ class Chain:
 
         if not self.fbm:
 
-            if state == 10:
+            if state != 8:
 
                 return np.zeros(l)
 

### 2020-01-15 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Updated tex with MRS7 comments.
Simplifying solute flux section

@@
 %MRS6: I would focus first on the outputs.  Not sure about the behavior/vs. selectivity.  Probably 
-% selelctivity since it's more results oriented. ``of varying complexity'' is unneeded in the titel
+% selelctivity since it's more results oriented. ``of varying complexity'' is unneeded in the tite
 %\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
@@
 % BJC6: The only issue with selectivity is that I don't think it would include a timescale.
-\title{Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores
+%MRS7: true, could just be ``predicting selectivity''
+\title{Capturing subdiffusive solute dynamics and predicting selectivity in nanoscale pores
 with time series modeling}
@@
   structure of positional fluctuations as a means of characterization and to 
-  allow us to predict solute MSDs. We show that our models reasonably reproduce
-  the MSDs calculated from MD simulations. Finally, we demonstrate how one can
-  use our models to estimate flux of a solute across a macroscopic-length pore
-  and, based on those quantities, the membrane's selectivity towards each solute.
-  Overall, this work helps to connect microscopic chemically-dependent solute 
+  allow us to predict solute MSDs. We show that both models reasonably reproduce
+  the MSDs calculated from MD simulations. 
+  %BJC7: added  
+  However, qualitative differences between MD and simulated MSDDM trajectories
+  may limit its usefulness. 
+  Finally, we demonstrate how one can use our models to estimate flux of a solute
+  across a macroscopic-length pore and, based on those quantities, the membrane's selectivity towards each solute.
+  This work helps to connect microscopic chemically-dependent solute 
   motions and macroscopic membrane performance.
@@
   of LLC monomers in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
-  Two general types of LLC membranes are being actively developed. The inverted hexagonal, 
+  Two general morphologies of LLC membranes are being actively developed. The inverted hexagonal, 
   H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
@@
   its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
-  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.
+  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.~\cite{hatakeyama_nanoporous_2010}
 
@@
 
-  In our previous work, we used molecular dynamics (MD) simulations to study the transport
-  of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
+  In our previous work,~\cite{coscia_chemically_2019} we used molecular dynamics (MD) 
+  simulations to study the transport of 20 small polar molecules in an H\textsubscript{II}
+  phase LLC membrane.
   %MRS6: sentence seems out of place here? True, but does it support the thesis here?
@@
   % eliminating the sentence.
+  %MRS6: It was also becasue they thought it was more likely to be interesting initially.  I'm in favor of 
+  % cutting for simplicity. 
   We chose to study the H\textsubscript{II} phase because it is a simpler geometry to model than 
@@
   %BJC4: Added next two paragraphs to help ease more into time series modeling
-  So far, our molecular models have provided valuable qualitative mechanistic insight 
-  with some quantitative support which already allows us to speculate about new LLC
-  monomer designs. However, they would be of greater value to a larger set of 
-  researchers if we could provide quantitative predictions of macroscopic observables
-  such as solute flux and selectivity. Due to the size of the types of systems we are 
-  studying (at least 62,000 atoms) it is prohibitively expensive and time-consuming to
+  Up through our previous studies, our molecular models have provided valuable 
+  qualitative mechanistic insight with some quantitative support. This insight
+  already allows us to speculate about new LLC monomer designs. However, they 
+  would be of greater value to a larger set of researchers if we could provide 
+  quantitative predictions of macroscopic observables such as solute flux and 
+  selectivity. Due to the size of the types of systems we are studying (at least
+  (62,000 atoms) it is prohibitively expensive and time-consuming to
   run simulations longer than those performed for this work ($\sim$5 $\mu$s). 
@@
   The complexity of a well-fit model generally parallels the complexity of the transport 
-  mechanism at hand, as well as the transport information the model conveys.
+  mechanism being studied, as well as the transport information the model conveys.
   In dense homogeneous membranes, the solution-diffusion model can extract 
@@
   ease and lower uncertainties. Fortunately, there is an abundance of information encoded
-  in the complex solute trajectories. Into a
-  model, we can incorporate fluctuations and time-dependent correlations in solute
-  position as well as the length of time solutes are trapped. We can add further
+  in the complex solute trajectories. We can incorporate fluctuations and time-dependent 
+  correlations in solute position as well as the length of time solutes are trapped into a
+  model. We can add further
   detail by integrating our time series analysis with our knowledge of the primary
@@
   %BJC4: added citations of prominent anomalous diffusion work
-  Researchers have developed a rigorous theoretical foundation for describing the 
-  motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
-  \cite{metzler_random_2000,bouchaud_anomalous_1990} The tools introduced by 
-  fractional calculus are instrumental to this theory.~\cite{gorenflo_fractional_1997}
+  %BJC7: changed thesis to focus more on this paper
+  We constructed our first model by applying the rigorous theoretical foundation 
+  already developed to describe the motion of particles exhibiting non-Brownian, or
+  anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990}
+  The tools introduced by fractional calculus are instrumental to this theory.~\cite{gorenflo_fractional_1997}
   They allow us to generalize the normally linear diffusion equation to fractional
-  derivative orders, providing descriptions of a much more diverse set of behavior.~\cite{klages_anomalous_2008}
+  derivative orders, providing descriptions of a much more diverse set of behavior,
+  including subdiffusion, a type of anomalous diffusion exhibited by solutes in 
+  this study.~\cite{klages_anomalous_2008}
 
@@
   %BJC4: added mention of the anomalous subdiffusion model we chose 
-  Our first modeling approach is based on the anomalous diffusion literature, 
-  applying the mathematical formalism describing subdiffusive transport to observed
-  solute trajectories. Specifically, we treated our system as an FBM process subordinate
-  to a CTRW, or subordinated FBM (sFBM) for short. We fit sFBM
+%  Our first modeling approach is based on the anomalous diffusion literature, 
+%  applying the mathematical formalism describing subdiffusive transport to observed
+%  solute trajectories. Specifically, 
+  %BJC7: with changes, above thesis statement is redundant
+  We treated our system as an FBM process subordinate to a CTRW, or subordinated 
+  FBM (sFBM) for short. We fit sFBM
   models in two ways: First, we parameterized solute motion using a single set of parameters fit
@@
 
-  Where applicable, the sFBM model is an elegant way to characterize single 
-  particle trajectories and in addition to providing an easy and efficient way to 
-  simulate solute trajectories, can help uncover the underlying solute-membrane
-  interactions which result in observed transport mechanisms. It can help 
-  researchers formulate hypotheses to explain why a certain set of parameters is
-  characteristic to a specific solute. Once one has knowledge of the primary 
-  mechanisms leading to anomalous diffusion behavior, one may gain additional
-  insight by formulating a state-based model.
-
-  % moved parts of method to here.
-  Markov state models (MSMs) are a popular class of models used to project long timescale
+  Where applicable, the sFBM model provides a way to propagate information about
+  solute trajectories gathered at the microsecond time scale to realistic experimental
+  time scales. It can also confirm the importance of assumed solute-membrane interactions
+  used to define the model's functional form, and suggest missing components. It
+  can help researchers formulate hypotheses to explain why a certain set of parameters
+  is characteristic to a specific solute.
+
+%   is an elegant way to characterize single 
+%  particle trajectories and in addition to providing an easy and efficient way to 
+%  simulate solute trajectories, 
+%  uncover the underlying solute-membrane interactions 
+%  which result in observed transport mechanisms.
+
+  % BJC7: moved last sentence of previous paragraph to here to make it more clear that
+  % we are moving to a new model
+  If one has knowledge of the primary mechanisms leading to anomalous diffusion behavior,
+  one may gain additional insight by formulating a state-based model, such as Markov state
+  models (MSMs). MSMs are a popular class of models used to project long timescale
   system properties based on molecular simulation trajectories by identifying
@@
   Standard MSMs are typically applied to determine equilibrium populations
-  of and the kinetics of transitions between various state configurations.~\cite{bowman_using_2009} 
+  of states and the kinetics of transitions between those states.~\cite{bowman_using_2009} 
   We extend the framework to include state-dependent fluctuations and correlations in 
@@
   model. The parameters themselves should provide clues that help explain solute 
-  behavior in a coherent way. A model that successfully reproduces MD MSDs, but 
+  dynamics in a coherent way. A model that successfully reproduces MD MSDs, but 
   with nonsensical parameters has severely diminished value as it could be a 
-  consequence of luck.
+  consequence of overfitting.
 
@@
   We evaluate the two modeling approaches by using them to characterize the dynamical
-  behavior of the four fastest moving solutes studied in our previous work.
-  Specifically, we study methanol, urea, ethylene glycol and acetic acid. In addition
+  behavior of the four fastest moving solutes studied in our previous work:
+  methanol, urea, ethylene glycol and acetic acid. In addition
   to moving quickly, allowing them to extensively explore membrane structural space,
@@
   focus our study on the 10 wt\% water system because solutes move significantly 
-  faster than in the 5 wt\% system studied previously. Appropriate stochastic 
-  modeling requires that solutes sample the accessible mechanisms with representative
-  probability.
+  faster than in the 5 wt\% system studied previously thus allowing more statistically
+  valid analyses.
+%  . Appropriate stochastic 
+%  modeling requires that solutes sample the accessible mechanisms with representative
+%  probability.
 
@@
   created a separate system and to each system we added 6 solutes per pore 
-  for a total of 24 solutes. This number of solutes per pore provides a balance
-  of a low degree of interaction between solutes, since we are primarily interested 
-  in solute-membrane interactions at present, as well as a sufficient amount of 
-  data from which to generate statistics on the time scales which we simulate.
+  for a total of 24 solutes. On the time scales which we simulate, this number
+  of solutes per pore provides a a sufficient amount of data from which to 
+  generate statistics. It also maintains a low degree of interaction between
+  solutes since, at present, we are primarily interested in solute-membrane 
+  interactions.
+%  balance
+%  of a low degree of interaction between solutes, since we are primarily interested 
+%  in solute-membrane interactions at present, as well as a sufficient amount of 
+%  data from which to generate statistics on the time scales which we simulate.
   Further details on the setup and equilibration of these systems are described in
@@
   We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
-  to collect ample data. We simulated the system with a time step of 2 fs at a pressure
-  of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and the v-rescale 
-  thermostat respectively. We recorded frames every 0.5 ns.
+  to collect ample data. We ran MD simulations using the leapfrog integrator with 
+  h-bonds constrained by the LINCS algorithm. We simulated a time step of 2 fs at
+  a pressure of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and
+  the v-rescale thermostat respectively. We recorded frames every 0.5 ns.
 
@@
   %BJC6: reorganized a little and broke into paragraphs meant to convey separate ideas.
-
+  %MRS7: definitely improved, I had a couple of comments to further refine.
   One can measure MSD in two ways. The time-averaged MSD measures all observed
@@
   %BJC6: I could move these MLE equations to Supporting  
+  %MRS7: for PRE, can leave in.
   \begin{equation}
@@
 
-  \textit{Correlated hop length distributions:} The marginal distribution of hops by solutes 
-  undergoing an sFBM process is Gaussian, therefore we parameterize it by its standard deviation, 
-  $\sigma$.~\cite{metzler_random_2000, metzler_anomalous_2014,neusius_subdiffusion_2009}
-  The measured mean is always very close to zero so we assume that it is exactly zero
-  in our time series simulations since we have no reason to expect drift in either direction
-  based on pore symmetry.
+  \textit{Correlated hop length distributions:} The marginal distribution of hop 
+  lengths by solutes undergoing an sFBM process is Gaussian, therefore we 
+  parameterize it by its standard deviation, $\sigma$.
+  ~\cite{metzler_random_2000, metzler_anomalous_2014,neusius_subdiffusion_2009}
+  The measured mean of the hop length distribution is always very close to zero so
+  we assume that it is exactly zero in our time series simulations since we have 
+  no reason to expect drift in either direction based on pore symmetry.
 
@@
   %BJC6: I could move the following to supporting and keep last sentence.
+  %MRS7: could simplify down to saying that it's hard to estimate when H > 0.5, but you only have to deal with H < 0.5, so the difficulties are not relevant. 
   There are many methods
@@
   the pore versus while in the tail region. This suggest two anomalous diffusion 
-  models of varying complexity. We created a simple, single mode model with a single 
-  set of parameters fit to solute trajectories.
+  models of varying complexity. We first create a simple, single mode model with
+  a single set of parameters fit to solute trajectories.
   Our second, two mode model assigns a set of parameters to each of 2 modes based
   on the solute's radial location. We define the first mode as the pore region, 
-  defined as less than 0.75 nm from any pore center. All else are in the second mode, the
-  tail region. We determined this cut-off by maximizing the difference in dynamical behavior as 
+  defined as less than 0.75 nm from any pore center. Solutes outside the pore 
+  region are in the second mode, the tail region. We determined this cut-off by
+  maximizing the difference in dynamical behavior as 
   described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
   there were not enough sufficiently long sequences of hops in each mode to reliably
-  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
-  single mode model for both modes of the two mode model.
-
-  % BJC3: A small figure describing above might be useful, or maybe point to a figure in supporting info
+  calculate a Hurst parameter for each mode so we used the single, average Hurst 
+  parameter from the single mode model for both modes of the two mode model.
 
@@
   between modes, meaning each transition had no memory of previously visited modes. 
-  We populated a 2$\times$2 count matrix by incrementing the appropriate entry by 1 each time step. 
-  For example, if we observed the solute in the tails followed by a transition to 
-  the pores, we incremented the $(2, 1)$ entry of the count matrix by 1. We generated
-  the transition probability matrix from the count matrix by normalizing the 
-  entries in each row so that they summed to unity.
-
-  %MRS4: Do you assume Markovian behavior in transitions between the states?  Be explicit.
-  %BJC4: Yes, added sentence directly after thesis above
+  We populated a 2$\times$2 count matrix by incrementing the appropriate entry by 1 
+  each time step 
+% For example, if we observed the solute in the tails followed by a transition to 
+% the pores, we incremented the $(2, 1)$ entry of the count matrix by 1.
+% We generated
+  and then generated a transition probability matrix by normalizing the entries
+  in each row of the count matrix so that they summed to unity.
 
@@
   %BJC6: added this. Not sure how much detail is necessary
+  %MRS7: seems fine.
   We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
@@
   ensemble of trajectories and then calculated the MSD of the subset. We reported 
-  the time-averaged MSD up to a 1000 ns time lag with corresponding 95\% confidence
+  the time-averaged MSD up to a 1000 ns time lag with corresponding 1$\sigma$ confidence
   intervals. 
+  %MRS6: somewhere you do talk about agreement to within 1 sigma
+  %instead of 95%, so probably should check for consistance.
 
@@
   atoms is less than 3.5 \AA~and the angle formed by $D-H \cdots A$ is less than
-  30$\degree$. We define a sodium ion to be associated with an atom if they are 
-  within 2.5 \AA~of each other, as determined in our previous work~\cite{coscia_chemically_2019}
+  30$\degree$.~\cite{luzar_effect_1996} We define a sodium ion to be associated 
+  with an atom if they are within 2.5 \AA~of each other, as determined in our 
+  previous work~\cite{coscia_chemically_2019}
 
@@
 
-  We constructed the state transition probability matrix, $T$, based on observed solute trajectories.
-  Using methods described in our previous work, we determined each solute's radial location 
-  and which, if any, trapping mechanisms affected it at each time step, then assigned the 
-  observation to a specific state according to the definitions in Table~\ref{table:states}.~\cite{coscia_chemically_2019}
-  Analogous to the mode transition matrix in Section~\ref{method:model_sFBM}, and based on
-  the current and previous state observation, we incremented the appropriate entry of an
-  $n~\times~n$ count matrix by 1, where $n$ is the number of states.
+  We constructed the state transition probability matrix, $T$, based on observed 
+  solute trajectories. Using methods described in our previous work, we determined 
+  each solute's radial location and which, if any, trapping mechanisms affected 
+  it at each time step, then assigned the observation to a specific state according
+  to the definitions in Table~\ref{table:states}.~\cite{coscia_chemically_2019}
+  Analogous to the mode transition matrix in Section~\ref{method:model_sFBM}, and 
+  based on the current and previous state observation, we incremented the appropriate
+  entry of an $n~\times~n$ count matrix by 1, where $n$ is the number of states. We
+  verified the Markovianity of state transitions as described in 
+  Section~\ref{S-section:markov_validation} of the Supporting Information.
 
   %BJC6: could defer most of this to supporting.  
-  We verified the Markovianity of state transitions by solutes in our MD simulations 
-  by analyzing the empirically measured transition matrix. An important condition
-  of a Markov process is the satisfaction of detailed balance:
-  \begin{equation}
-  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
-  \end{equation}
-  where $P$ is the equilibrium distribution of states. In other words, the number of
-  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
-  test is to verify that $T$ holds up to coarser time scale partitioning. As long as solutes
-  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
-  with time.~\cite{swope_describing_2004} We verified these properties 
-  in Section~\ref{S-section:markov_validation} of the Supporting Information.
+  %MRS7: yeah, supporting.
+Should just be ``Verified the Markovianity of state transitions in MD as described in Section [X].
+Generally, how one did verification of most things can be put in supporing, since that's not central to the argument.
+''
+%  We verified the Markovianity of state transitions by solutes in our MD simulations 
+%  by analyzing the empirically measured transition matrix. An important condition
+%  of a Markov process is the satisfaction of detailed balance:
+%  \begin{equation}
+%  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
+%  \end{equation}
+%  where $P$ is the equilibrium distribution of states. In other words, the number of
+%  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
+%  test is to verify that $T$ holds up to coarser time scale partitioning. As long as solutes
+%  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
+%  with time.~\cite{swope_describing_2004} We verified these properties 
+%  in Section~\ref{S-section:markov_validation} of the Supporting Information.
 
@@
 
-  We determined the rate at which solutes cross macroscopic-length pores based on the
+  We determine the rate at which solutes cross macroscopic-length pores based on the
   Hill relation:~\cite{hill_free_1989}
@@
   For computational reasons dependent on the model used, we simulated 1,000-10,000 trajectory
-  realizations, released at the pore entrance ($z=0$). 
-  %BJC6: next two sentences might not be necessary  
-  In the case of 
+  realizations, released at the pore entrance ($z=0$). In the case of 
   uncorrelated hops, one can continuously draw from the hop length distribution until 
@@
 
-  %BJC6: could probably remove this paragraph.
   We calculated the expected value of analytical fits to the passage time distributions
@@
 
-  To come up with an analytical equation describing the passage time distributions, 
+  To derive an analytical equation describing the passage time distributions, 
   one can frame the 
@@
 
-%    $$ A_i = \frac{J}{(\Delta P - \Delta \pi)} $$
-%  $$ S = \frac{A_i}{A_j} for a given pore length, L$$
-%  $$J = A(\Delta P - \Delta \pi)$$
-%  $$A = \frac{P_i}{L} $$
-%  $$P_i = \frac{flux}{drivingforce \cdot L} [=] \frac{particles}{s \cdot bar \cdot L}$$
-
-  %BJC4: we have better ways of getting peaks now
-%  In the absence of an analytical equation for the MFPT, we instead report the location of
-%  the peak of the passage time distribution. This has the added advantage of treating
-%  cases where the passage time distribution diverges and no mean exists. While we will
-%  call the peak in the distribution the MFPT, it is important to recognize that this 
-%  value is more representative of a typical passage time rather than a mean.
-
-  % BJC: concentration profile stuff
-%  One would then segment the trajectory
-%  each time it crosses $0$ and reflect all of the negative trajectories. The ensemble of
-%  trajectories is consistent with the fraction of partic
-
-%MRS6: maybe more subsections in results so people can get a sense of where the flow is going at a glance?
   \section{Results and Discussion}
@@
   anti-correlation between hops suggests a fractional diffusion process is subordinate 
-  to the CTRW. We believe the subordinated process is FBM or FLM because their analytical
-  correlation structures are close to those observed in our simulations (Figure~\ref{fig:hop_acf}).
-  Fractional motion is common in crowded viscoelastic environments where movement is highly 
+  to the CTRW. Of the different models, a process subordinated by FBM or FLM is best 
+  supported by the data because the analytical correlation structures of hop lengths are
+  close to those observed in our simulations (Figure~\ref{fig:hop_acf}). Fractional 
+  motion is common in crowded viscoelastic environments where movement is highly 
   influenced by the movement of surrounding components, such as monomer tails in our 
@@
   \includegraphics[width=\textwidth]{URE_trajectories.pdf}
-  \caption{Urea}\label{fig:URE_trajectories}
+  \caption{urea}\label{fig:URE_trajectories}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
-  \caption{Ethylene glycol}\label{fig:GCL_trajectories}
-  %BJC6: ^^ Should I capitalize glycol?
+  \caption{ethylene glycol}\label{fig:GCL_trajectories}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{MET_trajectories.pdf}
-  \caption{Methanol}\label{fig:MET_trajectories}
+  \caption{methanol}\label{fig:MET_trajectories}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
-  \caption{Acetic acid}\label{fig:ACH_trajectories}
+  \caption{acetic acid}\label{fig:ACH_trajectories}
   \end{subfigure}
@@
   between periods of entrapment, characteristic of a CTRW. Solute dynamics show
-  radial dependence. The longest periods of entrapment typically occur when 
-  solutes drift far from the pore center and into the tails.
+  radial dependence, represented by the color at each time point. The longest 
+  periods of entrapment typically occur when solutes drift far from the pore 
+  center and into the tails.
   }\label{fig:solute_trajectories}
@@
   \end{subfigure}
-  \caption{Using urea as an example, (a) the distribution of hop lengths fits well to 
+  \caption{Using urea as an example, (a) the distribution of hop lengths can be fit by 
   a Gaussian as well as a more general L\'evy stable distribution. The L\'evy stable
@@
 
-%  \begin{figure}
-%  \centering
-%  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
-%  % /figures/solute_trajectories.py
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{URE_trajectories.pdf}
-%  \caption{}\label{fig:solute_trajectories}
-%  \end{subfigure}
-%  % Next 3: /figures/sfbm_distributions
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
-%  \caption{}\label{fig:hop_distribution_comparison}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
-%  \caption{}\label{fig:powerlaw}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
-%  \caption{}\label{fig:hop_acf}
-%  \end{subfigure}
-%  \caption{(a) Urea exhibits hops between periods of entrapment, characteristic of a CTRW. 
-%  (b) The distribution of hop lengths fits well to a Gaussian as well as a more general L\'evy 
-%  stable distribution. The L\'evy stable distribution does a better job of capturing the 
-%  heavier tails and increased density near 0. (c) The distribution of dwell times is fit
-%  well by a power law but it may over-estimate the probability density at long dwell times.
-%  A power law truncated with an exponential cut-off may better describe the probability of
-%  long dwell times in our simulations. (d) The hops are negatively correlated to their previous
-%  hop. In combination, (a) -- (d) support modeling solutes as subordinated fractional Brownian
-%  and L\'evy motion. The behavior shown by urea in this figure is common to all solutes in this study (see
-%  Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops} of the
-%  Supporting Information).}\label{fig:anticorrelated_hops}
-%  %MRS4: are there similar figures in the supporting information.
-%  %BJC4: added
-%  %MRS6: I'm wondering if the other plots should be in the main text.  They are part of the core of the paper, showing that the modeling is reasonable. 
-%  \end{figure}
-
   We modeled the distributions of hop lengths in two ways. First, we assumed the 
@@
   the MLE fits of both on top of urea's hop length distribution in 
-  Figure~\ref{fig:hop_distribution_comparison}. 
-  %BJC6: I say the next sentence in plot
-  The L\'evy distribution does a better job capturing the somewhat heavy tails and 
-  high density near 0 of the hop length distribution.
-  However, since there are no known exact simulation techniques for generating 
-  realizations of fractional L\'evy motion, we must evaluate whether this more general
-  fit is worthwhile.
+  Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a 
+  better job capturing the somewhat heavy tails and high density near 0 of the hop
+  length distribution. However, since there are no known exact simulation techniques
+  for generating realizations of fractional L\'evy motion, we must evaluate whether
+  this more general fit is worthwhile.
 
@@
   made with these models consistently under-predict the MD MSDs (see 
-  Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supporting Information), therefore 
+  Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supporting Information). Therefore, 
   we will not include the pure sFBM or sFLM models in the remainder of our analysis.
@@
   \end{subfigure}
-  \caption{(a) Simulated urea trajectories generated by each variation on the 1 mode AD model 
-  display qualitatively similar hopping and trapping behavior to that shown in Figure~\ref{fig:solute_trajectories}. 
-  Dwell times are exaggerated in the sFBM and sFLM models because the power law dwell
-  time distributions are not truncated and have infinite variance. In (b) and (c) we 
-  compare additional trajectories simulated with the sFBMcut and sFLMcut models (blue) to
-  MD solute trajectories (black).  
-  %Analogous plots are shown for other solutes
-  %MRS6: I don't think the comparison between the cut and no cut are that interesting for the main text.  Move to supporting?
-  %MRS6: comparisons between modeled and actual trajectories side by side would be more interesting. 
-  %BJC5: todo: add plots to SI. Show I add a 2 mode model plot?
-  %and the 2 mode model in the Supporting Information. 
+  \caption{(a) Simulated urea trajectories generated by each of the four variations of 
+  the one mode AD model display qualitatively similar hopping and trapping behavior to
+  that shown in Figure~\ref{fig:solute_trajectories}. Dwell times are exaggerated in 
+  the sFBM and sFLM models because the power law dwell time distributions are not 
+  truncated and have infinite variance. In (b) and (c) we compare additional 
+  trajectories simulated with the sFBMcut and sFLMcut models (blue) to
+  MD solute trajectories (black). Trajectories are vertically offset for visual clarity.
   }\label{fig:ad_eyetest}
@@
   ``equilibrated" simulation time. Ethylene glycol and methanol show considerable 
-  differences in their MSDs. Urea and acetic acid appear to demonstrate satisfactory
-  stationarity. The shapes of their MSDs curves are also very similar (see 
+  differences between the MSDs of the two halves. Urea and acetic acid appear to demonstrate satisfactory
+  stationarity. The shapes of their MSD curves are also very similar (see 
   Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
@@
                            & First Half       & Second Half      \\\hline
-  Urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
-  Ethylene Glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
-  Methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
-  Acetic Acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
+  urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
+  ethylene glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
+  methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
+  acetic acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
 
@@
 
-  % BJC6: These next two paragraphs are a bit awkward without the figure being present. Not sure what the best course of action is.
-  Given stationary data, the AD model has satisfactory predictive capabilities. In 
-  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized 
+  Given stationary data, the AD model is capable of predicting solute MSDs 
+  measured from MD simulations within or near statistical uncertainty.
+  In Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized 
   the AD model using the first half of the stationary solute equilibrated trajectories 
@@
   the remainder of this work, we will employ parameters fit to the entire
-  equilibrated portion of the solute trajectories.%, doubling the data.
+  equilibrated portion of the solute trajectories. Even doubling the data might 
+  not be good enough for molecules with statistical non-stationarity, so we admit that 
+  those will only be approximations.
 
@@
   We obtain reasonable predictions of the MD simulated MSDs when we parameterize the AD 
-  model with all available data after the perceived equilibration time. Although we 
+  model with all available data after the perceived equilibration time. 
+  %BJC7: delete following sentence? I basically just said it above.  
+  Although we 
   concluded that methanol and ethylene glycol trajectories may not yet be stationary, we 
@@
 
-  %BJC6: combined 1 and 2 mode models. Easier to compare between and takes up less space. maybe a little cluttered with acetic acid.
   \begin{figure}
@@
   \end{subfigure}
-  \caption{In most cases, MSDs generated from realizations of our 1 and 2 mode AD 
-  models lie within or near the 1$\sigma$ confidence intervals of MD-generated 
+  \caption{In most cases, MSDs generated from realizations of both the one and two
+  mode AD models lie within or near the 1$\sigma$ confidence intervals of MD-generated 
   data. Drawing hops from a truncated L\'evy stable distribution (sFLMcut) yields
   MSDs similar to  when hops are drawn from Gaussian distributions (sFBMcut). 
-  In most cases, the 1 mode simulated MSDs are under-predicted at long timescales
-  because they show pronounced curvature which the MD MSDs lack. The 2 mode predictions
-  show less curvature than the 1 mode MSDs because the hop correlation structure
-  is broken every time a transition between tails occurs.
+  In most cases, the one mode simulated MSDs under-predicted the mean at long timescales
+  partially because they show pronounced curvature which the MD MSDs lack. The two mode
+  predictions show less curvature than the one mode MSDs because the hop correlation 
+  structure is broken every time a transition between tails occurs.
   }\label{fig:anomalous_msds}
@@
   \end{subfigure}
-  \caption{The parameters of the 1 mode model reveal differences in solute dynamics.
+  \caption{The parameters of the one mode model reveal differences in solute dynamics.
   (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, and L\'evy stable, 
@@
 
-  After a 1000 ns time lag, the 1 and 2 mode AD models do a fairly good job of 
+  After a 1000 ns time lag, the one and two mode AD models do a fairly good job of 
   predicting the magnitude of the MD MSD curves.
@@
   In most cases, the sFBMcut
-  and sFLMcut models give very similar results probably because their $\alpha_h$
+  and sFLMcut models give very similar results, most likely because their $\alpha_h$
   parameter values are relatively close to 2, meaning the hop length distributions
@@
 
-  The deviation between the 1 mode MSD predictions and MD are primarily due
+  The deviation between the one mode MSD predictions and MD are primarily due
   to differences in their curvature at long time lags. The shape and magnitude of 
   the predicted curves appears accurate relative to MD at short time lags.  
-  However, they undershoot the mean MD MSD as the time lag increases. As 
+  However, the modeled trajectories undershoot the mean MD MSD as the time lag increases. As 
   discussed in the previous section, long time positional anti-correlation, on
-  the order of hundreds of $ns$, may not exist in the MD system which results 
-  in a shift from sub-linear to linear MSD behavior. Acetic acid exemplifies
-  this point. At first glance, acetic acid's predicted MSD appears to match the 
+  the order of hundreds of ns, may not exist in the MD system. Eventual loss of
+  correlation would result in a shift from sub-linear to linear MSD behavior. 
+  Acetic acid exemplifies this point. At first glance, acetic acid's predicted MSD appears to match the 
   curvature of MD quite well, but closer examination reveals that the MD MSD 
@@
 
-  The 2 mode models display curvature more consistent with MD but for non-physical
-  reasons. The width of the hop distribution changes every time a switch between
-  pores and tails occurs. We are unaware of an appropriate technique which can 
+  The two mode models display curvature more consistent with MD but for non-physical
+  reasons. Every time a switch between the pores and tails occurs, the width of the
+  distribution used to model hops changes. We are unaware of an appropriate technique which can 
   correlate hops that come from different hop distributions, therefore every 
@@
   switch between modes the least show predicted MSDs with the greatest curvature. 
-  Methanol spends $> 90\%$ of its time in the tails (see Figure~\ref{fig:AD_mode_occupation}),
+  Due to the much larger accessible volume, methanol spends $> 90\%$ of its time
+  in the hydrophobic tails (see Figure~\ref{fig:AD_mode_occupation}),
   so mode transitions are relatively rare and the predicted MSDs have significant 
@@
 
-  The model parameters for the 1 and 2 mode models tell stories about each solute's
+  The model parameters for the one and two mode models tell stories about each solute's
   behavior that help explain the difference between the MSDs of different solutes. 
@@
 
-  Turning first to the parameters of the 1 mode model, we can begin to break down the
+  Turning first to the parameters of the one mode model, we can begin to break down the
   trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
@@
 
-  We can use the 2 mode model to gain an even deeper understanding of solute behavior
+  We can use the two mode model to gain an even deeper understanding of solute behavior
   in the pore versus in the tails. It is clear that solutes are significantly slowed 
@@
   allows it to more easily partition into the tails while ethylene glycol prefers
-  the pore region due to its two hydrophilic hydroxyl groups. Meanwhile methanol 
-  spends 91\% of its time in the tails likely due to its small size.  
+  the pore region due to its two hydrophilic hydroxyl groups. In contrast, methanol 
+  spends 91\% of its time in the tails, likely due to its small size.  
   The value of $\alpha_h$ for urea and acetic acid in the tails is 1.50, meaning its hop distribution
-  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
-  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
-  structurally similar molecules, both planar with two heavy atoms attached to a 
+  is heavy tailed relative to ethylene glycol and methanol, whose $\alpha_h$ values are
+  1.90 and 1.85 respectively, which is more consistent with a Gaussian distribution ($\alpha$=2).
+  Acetic acid and urea are structurally similar molecules, both planar with two heavy atoms attached to a 
   carbonyl group. Their small size and rigid shape may allow them to occasionally slip
@@
   %BJC6: Could delete this paragraph or move an abridged version to conclusions
+  %MRS7: Good question.  Seemed OK when I was reading it. Summarizing what was found in this section.
+  %BJC7: I'll leave it here unless we really need to cut stuff.
   Overall, the AD model does a reasonable job of predicting solute MSDs and its 
@@
   The data strongly suggests that one must truncate the power law dwell time 
-  distributions in order to obtain accurate MSD estimates. We can further understand
+  distributions in order to obtain accurate MSD estimates. Trajectories generated 
+  by pure power laws are qualitatively non-physical. We can further understand
   solute dynamics by adding radially dependent parameter distributions as in the 
@@
   %BJC6: could delete this paragraph since described in methods
+  %MRS7: yeahm could say you created one for each solute, as described in the methods.
   To create an MSDDM for each solute, we determined the state sequence associated
@@
   versus in the pores, however this would lead to a broken correlation structure 
-  similar to that seen in the 2 mode AD model.
+  similar to that seen in the two mode AD model.
 
@@
   deviation of the emission distributions from Gaussian behavior is far more pronounced
-  than that seen in the hop length distributions of the previous section, therefore we 
+  than that seen in the hop length distributions of the previous section, and therefore we 
   did not consider the Gaussian case (see Figure~\ref{fig:gaussian_levy_comparison}).
-  The correlation structure between hops resembles that of FLM (Figure~\ref{fig:msddm_acf}).
+  The correlation structure between hops is consistent with that of FLM (Figure~\ref{fig:msddm_acf}).
   The parameters of the L\'evy stable distributions along with their Hurst parameters 
@@
   \end{subfigure}
-  \caption{(a) Emission distributions are non-Gaussian and heavy-tailed. Shown here is the
-  emission distribution for transitions between states. The maximum likelihood
-  Gaussian fit severely underestimates the empirical density of hops near and far from zero 
-  while overestimating the density of hops at intermediate values. (b) Jumps drawn from
-  the transition distribution are negatively correlated to each other. The normalized version 
-  of Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
+  \caption{(a) The emission distributions of hop lengths are non-Gaussian and 
+  heavy-tailed. Shown here is the emission distribution for transitions between
+  states. The maximum likelihood Gaussian fit severely underestimates the empirical
+  density of hops near and far from zero while overestimating the density of hops
+  at intermediate values. (b) Jumps drawn from the transition distribution are 
+  negatively correlated to each other. The normalized version of 
+  Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
   an appropriate way to model jumps.} \label{fig:msddm_emissions}
@@
   highly anti-correlated in trapped states. As the number of simultaneously influencing
-  trapping mechanisms increases, the Hurst parameter decreases. The Hurst parameter is
+  trapping mechanisms increases, the Hurst parameter, $H$, decreases. $H$ is
   highest during transitions between states (state T). (b) As more trapping mechanisms
-  simultaneously influence solutes, the width of the hop length distribution decreases.
+  simultaneously influence solutes, the width of the hop length distribution ($\sigma$) decreases.
   The largest hops occur when solutes are unbound in the pores. (c) The weight of the 
@@
   Most of a solute's MSD is a consequence of transitions between the 8 states
-  in Table~\ref{table:states}. Motion while trapped in a state is highly 
+  in Table~\ref{table:states}. Perfectly anti-correlated motion ($H$=0) results in
+  no contribution to the solute's MSD. Motion while trapped in a state is highly 
   anti-correlated as indicated by their consistently low Hurst parameters.
-  Perfectly anti-correlated motion ($H$=0) results in no contribution to the solute's
-  MSD. There is a weak negative trend in the Hurst parameter values as the number
+  There is a weak negative trend in the Hurst parameter values as the number
   of simultaneously influencing trapping mechanisms increases (Figure~\ref{fig:H_v_state}). 
-  Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
-  trapping mechanisms. Highly anti-correlated behavior in the pores in the absence of
-  any trapping mechanism is likely caused by collisions with monomer head groups 
-  within the pore region. The Hurst parameters for transitional (T) emissions are up to 
-  18 times higher than emissions from trapped states. The value of $\alpha_h$ for 
+  % BJC7: Following is unsupported by data and therefore just a hypothesis
+%  Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
+%  trapping mechanisms. Highly anti-correlated behavior in the pores in the absence of
+%  any trapping mechanism is likely caused by collisions with monomer head groups 
+%  within the pore region. 
+  The Hurst parameters for transitional (T) emissions are up to 18 times higher than
+  emissions from trapped states. The value of $\alpha_h$ for 
   transition emissions is also relatively low giving higher probabilities to larger hops.
@@
   MSDs (see Figure~\ref{fig:msddm_performance}). In most cases, the MSDDM predicts
-  the magnitude of the MD MSDs within their 1$\sigma$ confidence intervals. One 
-  could argue that the curves of ethylene glycol and urea are statistically 
-  indistinguishable. However, it's possible that they may diverge on longer 
-  timescales due to differences in their curvature. Similarly, methanol's MD MSD 
-  is nearly linear while the MSDDM prediction is curving downward implying that it
-  may underestimate the MSD on longer timescales.
+  the magnitude of the MD MSDs within their 1$\sigma$ confidence intervals. 
+  %One 
+  %could argue that the curves of ethylene glycol and urea are statistically 
+  %indistinguishable. However, it's possible that they may diverge on longer 
+  %timescales due to differences in their curvature. 
+%  Similarly, methanol's MD MSD 
+%  is nearly linear while the MSDDM prediction is curving downward implying that it
+%  may underestimate the MSD on longer timescales.
+
+% BJC: alt to next paragraph
+%  We hypothesize that the predicted MSD of acetic acid is severely over-estimated
+%  most likely due to under-estimation of hop anti-correlation ($H$ too high) in 
+%  addition to an over-estimate of its hop lengths ($\sigma$ and $\alpha_h$ too high). 
+%  Acetic acid's predicted MSD actually lies just within the lower bound of urea's MD
+%  MSD 1$\sigma$ confidence interval, but lower than the prediction of the MSDDM for 
+%  urea. In all states, the degree of anti-correlation between acetic acid's hops is 
+%  higher than urea's (lower $H$) which is consistent with a lower predicted MSD. Although
+%  consistent, based on the curvature in Figure~\ref{fig:ACH_msddm}, and difficulties
+%  parameterizing $H$, it is possible that we under-estimated hop anti-correlation. 
+%  The length of acetic acid's hops and weight on the tails of the hop length 
+%  distribution ($\sigma$ and $\alpha_h$ respectively) are greater than or equal to 
+%  urea's which is consistent with a higher predicted MSD. There is also the strong 
+%  possibility that the over-estimate is a consequence of lumping together all of 
+%  acetic acid's transitional hops into a single correlated distribution.
 
@@
   under-estimation of hop anti-correlation ($H$ too high) and an over-estimate of
-  its hop lengths ($\sigma$ too high). As stated earlier, most of a solute's 
-  motion is due to displacements during state transitions. Acetic acid has a 
-  transitional Hurst parameter close to urea's and a transitional $\sigma$ value
-  that is higher than urea's. This suggests that the heavier tails of urea's transitional
-  hop distribution (greater $\alpha_h$ value) are in large part responsible for 
-  urea's higher predicted MSD. Although, note that acetic acid's predicted MSD
-  actually lies just within the lower bound of urea's MD MSD 1$\sigma$ 
-  confidence interval. There is also the strong possibility that the over-estimate is
-  a consequence of lumping together all of acetic acid's transitional hops into
-  a single correlated distribution.
+  its hop lengths ($\sigma$ and $\alpha_h$ too high). Acetic acid's predicted MSD
+  actually lies just within the lower bound of urea's MD MSD 1$\sigma$ confidence
+  interval, but lower than the prediction of the MSDDM for urea. As stated earlier,
+  most of a solute’s motion modeled by the MSDDM is due to displacements during 
+  state transitions. Acetic
+  acid has a transitional Hurst parameter close to urea’s and transitional $\sigma$
+  and $\alpha_h$ values that are higher than urea’s. The primary reason that the MSDDM
+  predictions for acetic acid's MSD are lower than urea's appears to be because of
+  higher hop anti-correlation (lower $H$) in all states, including transitions. 
+  There is also the strong possibility that the over-estimate is a consequence of
+  lumping together all of acetic acid’s transitional hops into a single correlated
+  distribution.
 
@@
   The second reason is a consequence of using a single hop length distribution 
-  for transitions. Many transitions occur between two trapped states where the 
+  for transitions. This was necessary because we could not collect enough data
+  to fit all of the possible transition distributions and because we could not
+  correlate emissions coming from different hop distributions. 
+  Many transitions occur between two trapped states where the 
   transitional hops are actually very small. Our model ignores this physical 
@@
 
-  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
-  diffusion model and the MSDDM in order to demonstrate how one can use their 
-  realizations in order to calculate the flux (see section~\ref{method:mfpt}) 
-  of solutes given model parameters extracted from MD simulations. The 1-mode 
-  sFBMcut model generates predictions similar to the 1-mode sFLMcut model at 
-  a lower computational cost. We showed that the 2-mode AD model has a broken
-  correlation structure, so we do not consider it here.
+  We used the one mode sFBMcut (see Table~\ref{table:anomalous_models}) AD
+  model in order to demonstrate how one can use its realizations in order 
+  to calculate the flux (see section~\ref{method:mfpt}) of solutes given 
+  model parameters extracted from MD simulations. The one mode sFBMcut model
+  generates predictions similar to the one mode sFLMcut model at a lower 
+  computational cost. We do not consider the two mode AD model because it 
+  has a broken correlation structure and we do not consider the MSDDM because
+  its realizations do not display the expected hopping and trapping behavior.
 
@@
   of 1 day to simulate 10000 sFBMcut realizations of solutes traversing a 50 nm pore.
-  The computational requirements of the MSDDM can be greater than 10 times longer. 
-  For both models, the RAM requirements and performance scales greater than linearly
-  and thus would take an infeasible amount of memory and time to simulate transport 
-  through a pore over 100 times longer.
+  The RAM requirements and performance scales greater than linearly and thus would
+  take an infeasible amount of memory and time to simulate transport through a pore
+  over 100 times longer. One could improve performance significantly by simulating 
+  less trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting 
+  Information, we determined that one can simulate as few as 100 sFBMcut realizations
+  in order to parameterize Equation~\ref{eqn:flux_decay}. For better precision, we 
+  recommend simulating at least 1000 realizations. Even with an order of magnitude
+  decrease in number of trajectories, it is still infeasible to simulate
+  experimental-length pores.
 
@@
   \end{equation}
-  %while the MFPT scales as its inverse, $(1/c)L^{\beta}$.
-
-  %BJC: need simulations with increased length for L=35-50 nm pores of acetic acid and methanol
-  %BJC: see of clauset has better way of fitting t^-alpha (alpha might be too big)
-  %BJC: should have a paragraph about c -- roughly follows their MSDs.
+
   \begin{figure}
   \centering
-  %BJC5: TODO: make same figure for msddm
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.485\textwidth}
   \includegraphics[width=\textwidth]{fpt_distributions.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.485\textwidth}
   \includegraphics[width=\textwidth]{flux_curves.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{flux_curves_msddm.pdf}
-  \caption{MSDDM}\label{fig:flux_curves_msddm}
-  \end{subfigure}  
-  %MRS6: make clear the dots are experiment. 
   \caption{(a) The distributions of first passage times generated from the sFBMcut model
-  fit well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
-  solutes as well as the MSDDM in Figures~\ref{S-fig:ad_fpt_fits} and~\ref{S-fig:msddm_fpt_fits}
-  of the Supporting Information. (b) The single particle flux measured 
-  by the sFBMcut AD model and (c) the MSDDM decays with increasing pore length. 
-  The rankings of solute fluxes are consistent with the MSDs predicted by each model.
-  The ranking of the MSDDM is most consistent with MD MSDs. The MSDDM predicts higher
-  fluxes than the sFBMcut model. We fit the single particle solute flux versus pore
-  length, $L$, to a power law function of the form $AL^{-\beta}$ (dashed lines in (b)
-  and (c)). 
-%  Solutes with higher fluxes have higher values of $c$. Solutes with 
-%  smaller Hurst parameters, $H$, have larger values of $\beta$. (c) If we remove 
-%  correlation between hops (set $H$=0.5), the flux increases significantly and 
-%  $\beta \sim 2$ for all solutes independent of dwell distribution
-%  parameters.
+  fits well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
+  solutes in Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The 
+  single particle flux measured by the sFBMcut AD model decays with increasing pore 
+  length. The rankings of solute fluxes are consistent with the MSDs predicted by each
+  model. We fit the single particle solute flux versus pore length, $L$, to a power law
+  function of the form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
   }\label{fig:flux_curves}
@@
   %BJC6: could move this paragraph to supporting
-  We determined that it is only necessary to simulate 1000 realizations of each model
-  in order to parameterize Equation~\ref{eqn:flux_decay}. We used 10000 trajectory
-  realizations in order to generate each point in Figure~\ref{fig:flux_curves_ad}, 
-  however, in Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting information,
-  we show that one can still show statistically significant differences in solute 
-  flux, with minimal change to the mean flux values, using as few as 100 trajectory
-  realizations. For better precision, we recommend simulating at least 1000 realizations. 
-  Since the computational cost of the MSDDM is greater than the AD model, we generated
-  each point of the flux curves in Figure~\ref{fig:flux_curves_msddm} using only 1000
-  realizations at each pore length.
+  %MRS7: Could push more to supporting.  I think you just need to state that you ran with X number, as determined in the supporting, but because cheap did 10K for the non-MSDDM models.
+  %BJC7: Now that MSDDM is gone, and I have data for 10,000 sFBMcut trajectories, I added 
+  % a sentence to paragraph 2 before this one pointing to the SI.
+%  We determined that it is only necessary to simulate 1000 realizations of each model
+%  in order to parameterize Equation~\ref{eqn:flux_decay}. We used 10000 trajectory
+%  realizations in order to generate each point in Figure~\ref{fig:flux_curves_ad}, 
+%  however, in Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting information,
+%  we show that one can still show statistically significant differences in solute 
+%  flux, with minimal change to the mean flux values, using as few as 100 trajectory
+%  realizations. For better precision, we recommend simulating at least 1000 realizations. 
+%  Since the computational cost of the MSDDM is greater than the AD model, we generated
+%  each point of the flux curves in Figure~\ref{fig:flux_curves_msddm} using only 1000
+%  realizations at each pore length.
 
@@
   % BJC6: I'm not sure this sentence adds anything
+  %MRS7: reminding people the physics behind models can be useful, though, maybe put back in?
   %This makes intuitive sense since higher degrees of anti-correlation should slow the rate at which solutes
@@
   % BJC6: took out for now since I was questioning it. Can add back if reviewers ask about these considerations.
+  %MRS7: yeah, leave out for now.
 %  Of course, our approach to modeling LLC membrane selectivity neglects a number

### 2020-01-15 LLC_Membranes/analysis/sfbm_parameters.py

@@ -743,7 +743,7 @@ class SFBMParameters(object):
             fig, ax1 = plt.subplots(1, 1, figsize=(6, 5))
             ax = [ax1]
 
-        fontsize = 14
+        fontsize = 16
 
         for m in range(nmodes):
 

### 2020-01-16 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
final draft ready for review

@@
-\documentclass[12pt]{article}
-
-\usepackage{setspace}
-\doublespacing
+\documentclass[aps,pre,preprint,groupedaddress]{revtex4-2}
+\usepackage{CJK}
+
 \usepackage{multirow}
@@
 \usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
+\usepackage{caption}
 \usepackage{amsmath} % or simply amstext
@@
 \usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\newcommand{\colormap}{jet}  % colorbar to use
 \usepackage{cleveref}
@@
 
+\DeclareUnicodeCharacter{03C9}{$\omega$}
+\usepackage[english]{babel}
+
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
@@
 
-\usepackage{titlesec}
-\titleformat{\subsubsection}[runin]
-  {\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}
-
 \externaldocument[S-]{Supporting_Information}
 
-%BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
-%MRS6: I would focus first on the outputs.  Not sure about the behavior/vs. selectivity.  Probably 
-% selelctivity since it's more results oriented. ``of varying complexity'' is unneeded in the tite
-%\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
-%and Predicts Long Timescale Behavior in Nanoscale Pores.}
-% BJC6: The only issue with selectivity is that I don't think it would include a timescale.
-%MRS7: true, could just be ``predicting selectivity''
-\title{Capturing subdiffusive solute dynamics and predicting selectivity in nanoscale pores
-with time series modeling}
-\author{Benjamin J. Coscia \and Michael R. Shirts}
-
 \begin{document}
 
-  \graphicspath{{./figures/}}
-  \maketitle
-
-  %BJC6: I could make abstract margins smaller
+  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+  with Time Series Modeling}
+
+  \author{Benjamin J. Coscia}
+  \author{Michael R. Shirts}
+
+  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}
+
+  \date{\today}
+
   \begin{abstract}
@@
   dwell times, hop lengths between dwells and correlation between hops. We 
-  explore 2 variations of the anomalous diffusion model. The first variation
+  explore two variations of the anomalous diffusion model. The first variation
   applies a single set of parameters to the solute displacements and the second
-  applies 2 sets of parameters based on the solute's radial distance from the
+  applies two sets of parameters based on the solute's radial distance from the
   closest pore center. Next, we generalize Markov state models, treating the
@@
 
+  \maketitle
+
+  \graphicspath{{./figures/}}
+
   \section{Introduction}
-
-%  BJC4: Moved this paragraph to later
-%  Mathematical descriptions of transport in complex separations membranes are 
-%  a powerful way to understand mechanisms and formulate membrane design principles. 
-%  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
-%  The complexity of a model generally parallels the complexity of the transport 
-%  mechanism at hand, as well as the transport information the model conveys.
-%  In dense homogeneous membranes, the solution-diffusion model can extract 
-%  diffusion and partition coefficients and has successfully predicted solute 
-%  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
-%  models yield predictions of diffusion coefficients and solute transport rates 
-%  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
-%  tracking approaches take us beyond continuum modeling and allow us to 
-%  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
-%  level, one can use molecular dynamics (MD) simulations to study both single 
-%  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
-%  All of these approaches facilitate speculation on the molecular origins of separations
-%  by attempting to give a more intuitive understanding of how solutes move as a function
-%  of their environment, in turn suggesting experiments that could be performed.
 
@@
   passage of water vapor.~\cite{mondloch_destruction_2015}
-%  The pace at which we achieve these or any other selective separation goals will be 
-%  heavily influenced by the quality of insights gained by the modeling approaches above.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{membrane_profile.pdf}
+  \includegraphics[width=0.5\textwidth]{membrane_profile.pdf}
   \caption{}\label{fig:membrane_profile}
@@
   \end{figure}
+
+%  \begin{figure}
+%  \centering
+%  \subfloat[\label{fig:monomer_structure}]{%
+%  			\includegraphics[width=0.4\textwidth, valign=c]{NaGA3C11.pdf}%
+%  			\vphantom{\includegraphics[width=0.5\textwidth, valign=c]{membrane_profile.pdf}}
+%  			}\hfill
+%  \subfloat[\label{fig:membrane_profile}]{\includegraphics[width=0.5\textwidth, valign=c]{membrane_profile.pdf}}\hfill
+%  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
+%  hexagonal phase in the presence of water where the carboxylate head groups occupy the
+%  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
+%  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
+%  straight and uniform sized pores. Water present in the tail region is omitted 
+%  for clarity.}\label{fig:membrane_structure}
+%  \end{figure}
 
@@
   where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
-  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
-  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha < 1$
-  indicates a subdiffusive process, while values of $\alpha = 1$ and $\alpha > 1$ 
-  are characteristic of Brownian and superdiffusive motion respectively.
-
-  %MRS6: next paragraph could be clearer.  Maybe motivate at the beginning why the importance of time. vs. ensemble averated. It's sprung a sort of a surprise there's a difference 
-  %BJC6: reorganized a little and broke into paragraphs meant to convey separate ideas.
-  %MRS7: definitely improved, I had a couple of comments to further refine.
-  One can measure MSD in two ways. The time-averaged MSD measures all observed
-  displacements over time lag $\tau$: 
-  \begin{equation}
-  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
-  \label{eqn:tamsd}
-  \end{equation}
-  where T is the length of the trajectory. The ensemble averaged MSD measures
+  diffusion coefficient. In this work, we only consider the MSD with respect to
+  the solutes' center of mass $z$-coordinate, which is oriented along the pore 
+  axis. A value of $\alpha < 1$ indicates a subdiffusive process, while values
+  of $\alpha = 1$ and $\alpha > 1$ are characteristic of Brownian and 
+  superdiffusive motion respectively.
+
+  %BJC7: added following two paragraphs to clarify our usage of the MSD as a tool. Modified a bit below too  
+  While it is theoretically possible to extract the value of $\alpha$ by fitting
+  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
+  we do not simulate enough independent solute trajectories to obtain a reliable
+  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
+  time distributions described in subsequent sections.
+
+  We primarily use the MSD as a tool for calculating the average properties of 
+  solute trajectories. We only compare MSDs calculated from MD simulations to 
+  those generated from our models. We do not use them to calculate diffusion 
+  constants or to relate our simulations to experimental measurements. Therefore
+  it is only important that we use a consistent definition for calculating the MSD.
+%  This approach is valid if we adhere to a consistent definition for MSD 
+%  calculations.
+
+  One can measure MSD in two ways. The ensemble averaged MSD measures 
   displacements with respect to a particle's initial position:
@@
   Fits to the \textit{ensemble} averaged MSD will always reproduce the form of 
-  Equation~\ref{eqn:msd_form}.
+  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
+  displacements over time lag $\tau$: 
+  \begin{equation}
+  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
+  \label{eqn:tamsd}
+  \end{equation}
+  where T is the length of the trajectory.
+
+%  For a small number of solute 
+%  trajectories, this is a much more statistically robust measure of the 
+%  average distance a solute travels over time.
 
@@
   average, it is a more statistically robust measure of the average distance a 
-  solute travels over time. Although theoretically possible, we do not use the 
-  ensemble averaged MSD to calculate $\alpha$ because we can extract the same 
-  parameter with higher precision using the dwell time distributions as described below.
-
-%  Only the \textit{ensemble} averaged MSD will reproduce the form of 
-%  Equation~\ref{eqn:msd_form} in all cases.
+  solute travels over time. The ensemble MSD of only 24 solute trajectories would
+  have much higher uncertainties.
+
+%  It may be difficult to calculate  ensemble
+%  MSD to estimate $\alpha$ with only 24 solute trajectories.
 %  
-%  We analyzed the time-averaged MSD of the simulated trajectories by measuring
-%  all possible displacements over time lag $\tau$:
-%  \begin{equation}
-%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
-%  \end{equation}
-%  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
-%  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
-%  MSD is given by:
-%  \begin{equation}
-%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
-%  \label{eqn:ensemble_msd}
-%  \end{equation} 
-%  In a pure CTRW, for example, the power law distribution of trapping times leads to
-%  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
-%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
-%  law trapping behavior, the time between hops diverges so there is no characteristic
-%  measurement time scale of solute motion. In fact, as measurement time increases, the 
-%  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
-%  with trapping times on the order of the measurement time get incorporated into the 
-%  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
-%  because, compared to the ensemble average, it is a more statistically robust measure
-%  of the average distance a solute travels over time. 
-%  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
-%  Although theoretically possible, we do
-%  not use the MSD to calculate $\alpha$ because we can extract the same parameter 
-%  with higher precision using the dwell time distributions as described below.
-
-%  of the process is exhibits weak ergodicity breaking due to 
-%  If the underlying subdiffusive process is not ergodic, like a pure CTRW, the time
-%  averaged MSD becomes linear.
+%  Although theoretically possible, we do not use the 
+%  ensemble averaged MSD to calculate $\alpha$ because we can extract the same 
+%  parameter with higher precision using the dwell time distributions as described below.
 
@@
   parameter we calculated by maximizing the likelihood function: 
-  %BJC6: I could move these MLE equations to Supporting  
-  %MRS7: for PRE, can leave in.
   \begin{equation}
@@
   In order to directly compare our anomalous diffusion model to finite-length MD 
-  trajectories we need to bound the dwell time distribution. We do this by adding 
-  an exponential cut-off to the power law so the dwell time distribution is 
-  now proportional to $t^{-1 - \alpha}e^{-\lambda t}$.
+  trajectories we need to bound the dwell time distribution. A standard way of 
+  doing this, with easily estimated paramters, is by adding an exponential 
+  cut-off to the power law so the dwell time distribution is now proportional 
+  to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model.
   %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
@@
 
-  \subsection{Solute Flux}\label{section:mfpt}
+  \subsection{Solute Flux and Selectivity}\label{section:mfpt}
 
@@
   in order to parameterize Equation~\ref{eqn:flux_decay}. For better precision, we 
-  recommend simulating at least 1000 realizations. Even with an order of magnitude
-  decrease in number of trajectories, it is still infeasible to simulate
+  recommend simulating at least 1000 realizations. However, even with an order of 
+  magnitude decrease in number of trajectories, it is still infeasible to simulate
   experimental-length pores.
@@
   and used the expected value of the analytical equation to calculate flux from 
-  Equation~\ref{eqn:hill_relation}. As shown in Figures~\ref{fig:flux_curves_ad} and
-  \ref{fig:flux_curves_msddm}, the flux appears to scale according to a power law 
-  of the form:
+  Equation~\ref{eqn:hill_relation}. As shown in Figure~\ref{fig:flux_curves_ad}, 
+  the flux appears to scale according to a power law of the form:
   \begin{equation}
@@
   \includegraphics[width=\textwidth]{flux_curves.pdf}
-  \caption{sFBMcut}\label{fig:flux_curves_ad}
+  \caption{}\label{fig:flux_curves_ad}
   \end{subfigure}
   \caption{(a) The distributions of first passage times generated from the sFBMcut model
-  fits well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
+  fit well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
   solutes in Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The 
@@
   \end{figure}
-
-  % BJC: could use better color scheme. Maybe outline hurst parameters
-%  \begin{subfigure}{0.475\textwidth}
-%  \includegraphics[width=\textwidth]{c_parameters.pdf}
-%  \caption{}\label{fig:c_parameters}
-%  \end{subfigure}
-%  \begin{subfigure}{0.475\textwidth}
-%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
-%  \caption{}\label{fig:beta_parameters}
-%  \end{subfigure}
-%  \begin{subfigure}{0.475\textwidth}
-%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
-%  \caption{}\label{fig:mfpt_curves}
-%  \end{subfigure}
-  %BJC: going out to 3 decimal places seems silly
-  %BJC: might get closer to beta=2 if I use different curve fitting technique than fitting line to log-log
-%  \begin{subfigure}{0.325\textwidth}
-%  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
-%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
-%  \end{subfigure}
-%  \begin{subfigure}{0.475\textwidth}
-%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
-%  \caption{}\label{fig:mfpt_curves_brownian}
-%  \end{subfigure}
-  %MRS5: the b) pane is a little messy.  If c) is moved to the supporting, maybe can make b into two figures, and 
-  % have each just show 1 point?
 
@@
   The scaling of solute flux with pore length is primarily influenced by anti-correlation
-  between solute hops. In Figure~\ref{fig:beta}a, we show that $\beta$, as derived 
-  from the sFBMcut model, is inversely related to the Hurst parameter. 
-  % BJC6: I'm not sure this sentence adds anything
-  %MRS7: reminding people the physics behind models can be useful, though, maybe put back in?
-  %This makes intuitive sense since higher degrees of anti-correlation should slow the rate at which solutes
-  %cross the membrane pore. 
-  $\beta$, as derived from the MSDDM, appears approximately constant which is 
-  consistent with nearly invariant transitional Hurst parameters (see 
-  Figure~\ref{fig:H_v_state}). However, Figure~\ref{fig:beta}a does raise
-  the question as to why $\beta$ is so much lower than the sFBMcut model. The MSDDM 
-  is fundamentally similar to the AD model in that one makes correlated draws 
-  from a hop distribution, therefore, we should expect the $\beta$ value of the
-  MSDDM to be larger than that of Brownian motion.
-
-  The length dependence of solute flux ($\beta$) for the MSDDM is under-estimated 
-  primarily due to innaccuracies in the correlation structure of very long FLM 
-  trajectories. To generate the curves in Figure~\ref{fig:flux_curves_msddm}, we 
-  needed to correlate 25--1000 times more hops than for the MSD predictions in 
-  Figure~\ref{fig:msddm_performance}. To understand the behavior of the MSDDM, we 
-  studied the $\beta$ parameter derived from variations on the SFBMcut model 
-  (see Figure~\ref{fig:beta}a), since we can generate exact realizations of FBM. 
-  First, we removed anti-correlation between hops in the sFBMcut trajectory (set
-  $H$=0.5). The $\beta$ parameter drops to values similar to the MSDDM. When we 
-  remove hop anti-correlation \textit{and} dwell times between hops (set dwell 
-  times equal to 1), effectively simulating Brownian motion, we observe similar 
-  $\beta$ parameters. These two variations imply that the $\beta$ parameter is 
-  only a function of $H$ and not dependent on dwell times ($\alpha$, $\lambda$) 
-  or hop lengths ($\sigma$). In Section~\ref{S-section:beta_estimates} of the 
-  Supporting Information we expand on this explanation and show that replacing 
-  inexact FLM realizations with exact FBM realizations recovers the pore length
-  dependence of solute flux.
-
-  %Although the dwell times are
-  %insignificant compared to the AD model (compare Figures~\ref{fig:ad_eyetest} and
-  %\ref{fig:msddm_eyetest} for example), we have just shown
-
-%  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
-%  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
-%  Turning first to the model itself, we have designed it to ensure that the magnitude of the
-%  hops in the series of transitions between states are anti-correlated from start to finish. 
-%  This assumes that the transition correlation structure is unaffected by the
-%  sub-trajectories between each state transition. Each time a state transition occurs, one
-%  must initialize a new time series sub-trajectory with its own correlation structure. 
-%  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
-%  %in each state is relatively short making the accuracy of the correlation structure 
-%  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
-%  %$\sigma$ in trapped states. 
-%  Since we add the transitional hop lengths to each end of
-%  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
-%  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
-%  MSDDM to completely immobilize particles except when they transition between states. 
-%  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
-%  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
-%  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
-%  To generate the curves in Figure~\ref{fig:flux_curves_msddm}, we needed to correlate 
-%  25--1000 times more hops than for the MSD predictions in Figure~\ref{fig:msddm_performance}. 
-%  In short, it is computationally infeasible to use enough terms to accurately incorporate
-%  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
-%  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
-%  fractional Brownian motion, for which we have an exact simulation method, in place of 
-%  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
-%  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
-%  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
-%  of FLM.
-
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.43\textwidth}
-%  \includegraphics[width=\textwidth]{beta_hurst.pdf}
-%  \caption{}\label{fig:beta_hurst}
-%  \end{subfigure}
-%  \begin{subfigure}{0.52\textwidth}
-%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
-%  \caption{}\label{fig:beta_parameters}
-%  \end{subfigure}
-%  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
-%  %MRS6: should try to lead with what the overall results/conclusions are.
-What does it mean that parameters are larger or smaller?
-What should the reader take from the discussion?
-Should it be in supportinig?
-%  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
-%  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
-%  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
-%  sub-trajectories between state transitions decorrelate transitional hops and because
-%  our FLM simulation procedure does not accurately correlate hops after long time lags. 
-%  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
-%  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
-%  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
-%  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
-%  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
-%  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
-%  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
-%  \end{figure}
-
-  %BJC6: TODO: add (a), (b), (c)
+  between solute hops. In Figure~\ref{fig:beta}a, we show that $\beta$ is inversely 
+  related to the Hurst parameter. This makes intuitive sense since higher degrees of
+  anti-correlation should slow the rate at which solutes cross the membrane pore. 
+  When we remove anti-correlation between hops (set $H$=0.5), the length dependence 
+  becomes the same for all solutes, dropping to a value just below 2. This also 
+  implies that hop lengths and dwell times do not affect length dependence since 
+  each solute exhibits different hopping and trapping behavior yet are all parameterized
+  by the same value of $\beta$ when $H$=0.5.
+  %BJC7: is above argument enough to get rid of following sentence (and associated bar in the Figure)?
+  We further verified this claim by removing hop anti-correlation and setting all 
+  dwell times equal to one timestep, effectively simulating Brownian motion.
+  The length dependence remains unchanged.
+
+  %BJC6: TODO: add (a), (b), (c) labels
+  %BJC7: TODO: optimize figure dimensions
   \begin{figure}
@@
   \end{subfigure}
-  \begin{subfigure}{0.42\textwidth}
-  \vspace{-2em}
-  % use c_parameters2.py
+  \begin{subfigure}{0.31\textwidth}
+  % use c_parameters3.py
+  %BJC7: I could plot bars with the MSD of each solute to show that trend is same.
   \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.53\textwidth}
-  \vspace{-2em}
-  \vspace{0.5em}
+  \begin{subfigure}{0.66\textwidth}
+%  \vspace{-2em}
+%  \vspace{0.5em}
   \includegraphics[width=\textwidth]{c_influence.pdf}
@@
   \end{subfigure}
+  \vspace{-1.5cm}
   \caption{(top) Increased anti-correlation between hops (decreased $H$) appears to 
   increase the length-dependence of solute flux (higher $\beta$) for the sFBMcut model.
-  The length dependence of the MSDDM model is much weaker because sub-trajectories 
-  between state transitions decorrelate transitional hops and because our FLM 
-  simulation procedure does not accurately correlate hops after long time lags. 
-  We support this claim by removing hop correlation from the sFBMcut model which
-  results in a drop in the $\beta$ value close to MSDDM. These values of $\beta$ are
-  consistent with Brownian motion (no hop correlation and unit-length dwell times).
-  (bottom left) As solute flux increases, the scaling of the flux curves, $c$, increases 
-  (compare ranking with Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm}).
-  The $A$ parameters of the MSDDM are smaller than the sFBMcut AD model because the AD
-  model must compensate for its strong length dependence (higher $\beta$). 
+  If we remove anti-correlation, by setting $H$=0.5, the length dependence parameter
+  drops to a value near 2. When we remove hop anti-correlation and dwell times between
+  hops, effectively simulating Brownian motion, the $\beta$ parameter stays near 2. 
+  This suggests that $\beta$ does not depend on dwell times (parameterized by $\alpha$
+  and $\lambda$). (bottom left) As solute flux increases, the scaling of the flux 
+  curves, $A$, increases (compare ranking with Figure~\ref{fig:flux_curves_ad}).
   (bottom right) Physical processes which increase the rate of solute displacement 
@@
   parameterized by the sFBMcut AD model, and generated realizations of the
-  model by each parameter independently about the same base parameter set. 
-  %Therefore, the middle bars for these four 4 parameters are 
-  %generated from the same set of parameters. 
+  model by varying each parameter independently about the same base parameter set. 
+%  Therefore, the middle bars for these four 4 parameters are 
+%  generated from the same set of parameters. 
   Decreased dwell times (increased $\alpha$), increased hop lengths (increased 
@@
   lead to increases in $A$. 
-  %$c$ responds linearly to increases in $\sigma$ and $\lambda$
+  %$A$ responds linearly to increases in $\sigma$ and $\lambda$
   and non-linearly to $\alpha$.
   The data suggests that the $A$ parameters do not depend on hop anti-correlation ($H$).
-  To test $\alpha_h$, we used the set of parameters defining the MSDDM of Urea (since 
-  sFBMcut does not use a L\'evy distribution) and varied the $\alpha_h$ parameter of 
-  the transitional hops. As $\alpha_h$ increases, $A$ increases slightly since the 
-  density of the L\'evy stable PDF is shifted away from rare hops and broadened at 
-  its center. We expect similar dependence of $A$ on $\sigma$ and $H$ of the MSDDM.
   }\label{fig:beta}
@@
 
-  Parameters represented by physical processes which act to modify the rate at 
-  which solutes move through the membrane pores will affect the scaling pre-factor
-  of the solute flux curves ($A$). Comparison of Figure~\ref{fig:beta}b with 
-  Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm} reveals that
-  the ranking of the $A$ parameters is consistent with the ranking of solute 
-  flux. In general, $A$ values generated by the MSDDM model are smaller than the
-  those generated by the sFBMcut AD model because the AD model has to compensate
-  for high $\beta$ values. In Figure~\ref{fig:beta}c we demonstrate that 
-  decreasing dwell times (increasing $\alpha$), increasing hop lengths (increasing 
-  $\sigma$), cutting off the dwell time distribution at shorter times (increasing
-  $\lambda$) and increasing tail weights of the hop length distribution (decreasing
-  $\alpha_h$) independently lead to an increase in $A$. Figure~\ref{fig:beta}c
-  also suggests that $A$ is not dependent on hop anti-correlation ($H$).
-
-%  The values of $c$ are directly related to the magnitude of solute flux and, where
-%  applicable, are functions of $\sigma$, $\alpha$, $\lambda$ and $\alpha_h$. 
-%  In Figure~\ref{fig:beta}, we plot the $c$ values measured
-%  for each solute with each model from lowest to highest. In general, $c$ values generated
-%  by the MSDDM model are smaller than the those generated by the sFBMcut AD model 
-%  because the AD model has to compensate for high $\beta$ values. 
-%  Comparison 
-%  of Figure~\ref{fig:c_parameters} with Figures~\ref{fig:flux_curves_ad} 
-%  and~\ref{fig:flux_curves_msddm} reveals that the ranking of the $c$ parameters is
-%  consistent with the ranking of solute flux. 
-%  Therefore, it is reasonable to hypothesize
-%  that any parameter which acts to modify the rate at which solutes move through the
-%  membrane pores will affect $c$ for various physical reasons. 
-%  In 
-%  Figure~\ref{fig:c_influence} we demonstrate that decreased dwell times
-%  (increased $\alpha$), increased hop lengths (increased $\sigma$), cutting off the
-%  dwell time distribution at shorter times (increased $\lambda$) and decreased tail 
-%  weights of the hop length distribution (increased $\alpha_h$) independently lead to
-%  an increase in $c$. Figure~\ref{fig:c_influence} also suggests that $c$ is not dependent on hop
-%  anti-correlation ($H$).
-
-%  We showed earlier that $\beta$ is not a
-%  function of $\sigma$ or $\alpha$, therefore dwell times and hop lengths must
-%  influence $c$. In fact, any parameter which acts to modify the rate at which 
-%  solutes move through the membrane pores will affect $c$. Therefore it is 
-%  sensible to hypothesize that a higher degree of anti-correlation (lower $H$)
-%  should decrease $c$ and a higher value of $\alpha_h$ should also increase $c$.
-%  In Figure~\ref{fig:c_influence}, we verify these hypotheses by holding
-
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.42\textwidth}
-%  % use c_parameters2.py
-%  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
-%  \caption{}\label{fig:c_parameters}
-%  \end{subfigure}
-%  \begin{subfigure}{0.53\textwidth}
-%  \vspace{0.5em}
-%  \includegraphics[width=\textwidth]{c_influence.pdf}
-%  \caption{}\label{fig:c_influence}
-%  \end{subfigure}
-%  %BJC5: waiting on simulations for alpha_h
-%  \caption{(a) The $c$ parameter increases with solute flux (compare ranking with
-%  Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm}). The $c$ parameters
-%  of the MSDDM are smaller than the sFBMcut AD model because the AD model must
-%  compensate for its strong length dependence (higher $\beta$). (b) Changes to parameters
-%  which increase the rate of solute displacement result in larger values of $c$. 
-%  To test the dependence of $c$ on $\alpha$, $\sigma$, $H$ and $\lambda$, we chose a 
-%  single set of parameters, representative of solutes parameterized by the sFBMcut AD model,
-%  and generated realizations of the model by varying each parameter independently about the
-%  same base parameter set. Therefore, the middle bars for these four 4 parameters are 
-%  generated from the same set of parameters. Decreased dwell times (increased $\alpha$),
-%  increased hop lengths (increased $\sigma$), and a lower cut-off to the dwell time
-%  distribution (increased $\lambda$) lead to increases in $c$. $c$ responds linearly
-%  to increases in $\sigma$ and $\lambda$ and non-linearly to $\alpha$. The data 
-%  suggests that the $c$ parameters do not depend on hop anti-correlation ($H$). To test 
-%  $\alpha_h$, we used the set of parameters defining the MSDDM of Urea (since sFBMcut does
-%  not use a L\'evy distribution) and varied the $\alpha_h$ parameter of the transitional
-%  hops. As $\alpha_h$ increases, $c$ increases slightly since the density of the L\'evy
-%  stable PDF is shifted away from rare hops and broadened at its center.
-%  We expect similar dependence of $c$ on $\sigma$ and $H$ of the MSDDM.}\label{fig:c}
-%  \end{figure}
+%  Parameters represented by physical processes which act to modify the rate at 
+%  which solutes move through the membrane pores will affect the scaling pre-factor
+%  of the solute flux curves ($A$).
+
+  Dwell times and hop lengths directly modify the rate at which solutes move 
+  through the membrane pores and are reflected in the scaling pre-factor of
+  the solute flux curves, $A$. Comparison of Figure~\ref{fig:beta}b with 
+  Figure~\ref{fig:flux_curves_ad} reveals that the ranking of the $A$ parameters
+  is consistent with the ranking of solute flux. In Figure~\ref{fig:beta}c we
+  demonstrate that decreasing dwell times (increasing $\alpha$), cutting off 
+  the dwell time distribution at shorter times (increasing $\lambda$), and increasing 
+  hop lengths (increasing $\sigma$) independently lead to an increase in $A$. 
+  Figure~\ref{fig:beta}c also suggests that $A$ is not dependent on hop 
+  anti-correlation ($H$).
 
@@
 
-  In Figure~\ref{fig:selectivity}, we plot Equation~\ref{eqn:selectivity_ratio} for pore
-  lengths ranging from those studied in Figure~\ref{fig:flux_curves} to macroscopic-length
-  pores. 
-  %Greater differences in $\beta$ values leads to selectivities that are stronger 
-  %functions of pore length. 
-  For $(A_i / A_j)=1$, LLC membranes will be more selective towards passage of solutes 
-  with less anti-correlated hopping behavior (lower $\beta$). 
-  %versus those with high $\beta$ values.
-  For the same degree of hop anti-correlation, 
-  %When $\beta$ values are equal, 
-  as is the case for uncorrelated motion, selectivity only
-  depends on the pre-factors, $A$. In most cases, the length dependence of selectivity 
-  plateaus quickly which implies that a coating of LLC membrane with a thickness on the 
-  order of those already made experimentally should be sufficiently optimal.
-
   \begin{figure}
   \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{selectivity.pdf}
-  \caption{sFBMcut}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{selectivity_msddm.pdf}
-  \caption{MSDDM}
-  \end{subfigure}
+  \includegraphics[width=0.5\textwidth]{selectivity.pdf}
   \caption{The selectivity of 2 species changes monotonically with pore length. The
@@
   those predicted by the MSDDM (b) because predictions of the AD model result in a much
-  larger variation in flux (compare Figures~\ref{fig:flux_curves_ad} and~\ref{fig:flux_curves_msddm}).}
+  larger variation in flux (compare Figures~\ref{fig:flux_curves_ad}).}
   \label{fig:selectivity}
@@
 
-  The selectivities predicted by the sFBMcut model are both higher in magnitude and
-  ordered differently than the those predicted by the MSDDM. The magnitudes of the
-  sFBMcut predictions are higher because the predicted solute fluxes vary more widely
-  than those predicted by the MSDDM (compare Figures~\ref{fig:flux_curves_ad} 
-  and~\ref{fig:flux_curves_msddm}). The ordering is different mostly because the 
-  ordering of the flux predictions is different.
-
-  We cannot say with absolute certainty which selectivity curves are more 
-  trustworthy. The sFBMcut model uses exact simulation techniques and yields 
-  qualitatively accurate solute trajectories, but it may overestimate long 
-  timescale correlation present in the real system. For this reason, we might
-  expect the $\beta$ values of the true flux curves to be closer to the 
-  Brownian value as exhibited by the MSDDM. But the MSDDM yields qualitatively
-  inaccurate solute trajectories and we do not have a good understanding of
-  how to precisely control the point at which solute hops become decorrelated.
-
-  We may gain the most by using the two models in tandem. In both cases, the 
-  data suggests that this particular LLC membrane might be most useful for 
-  selectively separating ethylene glycol from acetic acid. Ethylene glycol
-  exhibits the highest flux while acetic acid has the lowest. Ethylene glycol
-  has the weakest dependence on pore length (lowest $\beta$) according to the
-  sFBMcut model, while acetic acid has the second highest dependence. This 
-  analysis certainly merits further experimental exploration.
+  In Figure~\ref{fig:selectivity}, we plot Equation~\ref{eqn:selectivity_ratio} for pore
+  lengths ranging from those studied in Figure~\ref{fig:flux_curves_ad} to macroscopic-length
+  pores. For the same degree of hop anti-correlation, as is the case for uncorrelated motion, 
+  selectivity depends on solute hop lengths and dwell times ($A$). For $(A_i / A_j)=1$, LLC
+  membranes will be more selective towards passage of solutes with less anti-correlated hopping
+  behavior (lower $\beta$). The selectivity towards solutes with less length dependent flux
+  increases with membrane thickness. In most cases, the length dependence of selectivity 
+  plateaus quickly which implies that a coating of LLC membrane with a thickness on the 
+  order of those already made experimentally should be sufficiently optimal.
+
+  %BJC7: I don't know why there is a big space before this paragraph when compiled
+  Of the solutes studied, the data suggests that this particular LLC membrane 
+  might be most useful for selectively separating ethylene glycol from methanol
+  and acetic acid. Relative to acetic acid, ethylene glycol takes larger hops 
+  and is trapped longer, leading to a larger $A$. There is also an appreciable 
+  difference in the scaling of each solute's flux with pore length ($\beta$) 
+  which gives the selectivity significant length dependence. Relative to methanol,
+  ethylene glycol takes similarly-sized hops and dwells which is why selectivity
+  is relatively low for very short pore lengths. However, the large difference in
+  hop correlation between the two solutes leads to the strongest pore length 
+  dependence of selectivity. 
+  %In both case, selectivity is enhanced as the pore 
+  %length increases which comes at the cost of lower solute flux, a phenomenon 
+  %ubiquitous in polymer separations membranes.~\cite{geise_water_2011}
+
+%  Ethylene glycol shows the least length dependent flux, likely because
+%  it spends the majority of its time in the pores (see Figure~\ref{fig:AD_mode_occupation}).
+%  %It also shows reasonable selectivity of Urea over acetic acid.  
+%  Ethylene glycol has the highest $c$ value and the lowest $\beta$ value. The high
+%  value of $c$ itself greatly enhances its selective passage. Even more importantly,
+%  the relatively large difference between its $\beta$ value and those of methanol 
+%  and acetic acid give rise to a strong pore length dependence. The selectivity is
+%  enhanced as the pore length increases at the cost of lower solute flux, a 
+%  phenomenon ubiquitous in polymer separations membranes.~\cite{geise_water_2011}
 
@@
 
-  In their current state, one should use the predictions of our models with caution.
+%  In their current state, one should use the predictions of our models with caution.
   Although large portions of the MSDs predicted by our models fall close to or 
@@
   single, relatively broad transition emission distribution prevent long periods of
-  immobility. The best solution to this would be to have individual emission distributions
-  for each type of transition, but this would require orders of magnitude more data. 
-  AD model realizations show appropriate qualitative behavior, but the persistent 
-  curvature of the computed MSD curves, due to the correlation structure of fractional 
-  motion, under-estimate the MD MSD curves which appear to be trending towards linear
-  on $\mu$s timescales. In the future, we could address this by implementing a truncation
-  to the positional auto-correlation function.
-
-  We demonstrated how one could used our models in order to to determine
+  immobility. The most obvious solution to this would be to generate individual emission
+  distributions for each type of transition, but this would require orders of magnitude
+  more data. This approach is further complicated by the need to make correlated draws
+  from a fractional L\'evy process with a frequently changing distribution width. 
+  A possible simplification could be to assume that correlation is lost every time a
+  state transition occurs.
+%  AD model realizations show appropriate qualitative behavior, but the persistent 
+%  curvature of the computed MSD curves, due to the correlation structure of fractional 
+%  motion, under-estimate the MD MSD curves which appear to be trending towards linear
+%  on $\mu$s timescales. In the future, we could address this by implementing a truncation
+%  to the positional auto-correlation function.
+
+  Although the AD model generates qualitatively accurate trajectories and 
+  predicts MSDs near or within the 1$\sigma$ confidence interval of our
+  MD simulations, the curvature of the predicted MSDs may not be consistent
+  with the MD simulations. The MSD curves calculated from MD simulations 
+  appear to straighten out on long timescales while those predicted by the
+  AD model continuously curve. This is because pure fractional Brownian motion
+  features hop correlation that persists indefinitely. We may be able to address
+  this by truncating the positional autocorrelation function, allowing 
+  correlation to diminish on the 100 ns timescale.
+
+  We demonstrated how one could use the one mode AD model in order to to determine
   macroscopic flux and selectivity. We showed that, when using the AD model, 
   solute flux decreases with pore length at a rate faster than pure 
-  Brownian motion due to anti-correlation between hops. However, using the
-  MSDDM, we observed a decay in flux similar to Brownian motion. This is
-  primarily due to the inexact method that we use to correlate hops of the 
-  fractional L\'evy motion process. 
-  %When we replace FLM with FBM in the 
-  %MSDDM algorithm, we observe a flux decay more consistent with that predicted
-  %by the AD model. 
-  We used the ratio of solute fluxes generated from each model in order to 
-  calculate selectivity. Due to differences in hop anti-correlation, we observe 
-  a length dependent selectivity. This length dependence may dissipate
-  once we gain a more complete understanding of the hop correlation structure. 
-  If the length dependence of a properly correlated model always converges to 
-  $\beta$=2, it will greatly influence the prediction of selectivity on 
-  macroscopic length scales.
+  Brownian motion due to anti-correlation between hops. We used the ratio of 
+  solute fluxes generated from each model in order to calculate selectivity. 
+  Due to differences in hop anti-correlation, we observe length dependent 
+  selectivity. Based on these calculations we can hypothesize that this 
+  particular LLC membrane may be a good candidate for the selective separation
+  of ethylene glycol from acetic acid or methanol.
+
+%  This length dependence may dissipate once we gain a more 
+%  complete understanding of the hop correlation structure. 
+%  If the length dependence of a properly correlated model always converges to 
+%  $\beta$=2, it will greatly influence the prediction of selectivity on 
+%  macroscopic length scales.
 %  However, this length dependence mostly plateaus at length scales that can be
@@
   to design LLC monomers for solute-specific separations by forcing us to think
-  in terms of controlling solute trapping. The anomalous diffusion model is 
+  in terms of controlling solute transport. The anomalous diffusion model is 
   quite flexible because it does not require knowledge of specific trapping 
@@
   to eliminate one source of trapping, then high selectivities are possible.
-  Overall, in tandem or separately, our models facilitate new ways of approaching
-  complex separation problems.
+  Our models facilitate new ways of approaching complex separation problems.
 
@@
   \section*{Acknowledgments}
+
+  We thank Richard Noble for helping us make the connection between the empirical 
+  mean first passage time distribution and the analytical equation to which we fit
+  the distributions (Equation~\ref{eqn:passage_times}).
+
   %MRS: add people who contributed non-author level ideas. 
@@
 
-  We would also like to thank Richard Noble for helping us make the connection 
-  between the empirical mean first passage time distribution and the analytical
-  equation to which we fit the distributions (Equation~\ref{eqn:passage_times}).
-
   %MRS6: look over and make bibliography consistent (i.e. no months, consistent journal abbreviations)
-  \bibliographystyle{ieeetr}
+  \bibliographystyle{apsrev4-2}
   \bibliography{stochastic_transport}

### 2020-01-16 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
final draft ready for review

--- 2020-01-08 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
@@
 \usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
+\usepackage{amsmath}
 \usepackage{siunitx}
@@
 \usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
 \newcommand{\colormap}{jet}  % colorbar to use
@@
 \usepackage{multirow}
+
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
@@
 
-\title{Supporting Information: Time Series Modeling of Varying Complexity Captures 
-Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.}
+\title{Supporting Information: Capturing Subdiffusive Solute Dynamics and 
+Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
 
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{msddm_fpt_distributions_URE.pdf}
-  \caption{Urea}\label{fig:URE_msddm_fpt_distributions}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{msddm_fpt_distributions_ACH.pdf}
-  \caption{Acetic Acid}\label{fig:ACH_msddm_fpt_distributions}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{msddm_fpt_distributions_GCL.pdf}
-  \caption{Ethylene Glycol}\label{fig:GCL_msddm_fpt_distributions}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{msddm_fpt_distributions_MET.pdf}
-  \caption{Methanol}\label{fig:MET_msddm_fpt_distributions}
-  \end{subfigure}
-  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
-  first passage time distributions generated by 1000 realizations of the 
-  Markov state dependent dynamical model. Note that we generated 10 times less
-  realizations of the MSDDM which leads to noisier histograms. We show that
-  this has a negligible effect on the fits in Figure~\ref{fig:flux_curve_sensitivity}.}\label{fig:msddm_fpt_fits}
-  \end{figure}
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{msddm_fpt_distributions_URE.pdf}
+%  \caption{Urea}\label{fig:URE_msddm_fpt_distributions}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{msddm_fpt_distributions_ACH.pdf}
+%  \caption{Acetic Acid}\label{fig:ACH_msddm_fpt_distributions}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{msddm_fpt_distributions_GCL.pdf}
+%  \caption{Ethylene Glycol}\label{fig:GCL_msddm_fpt_distributions}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{msddm_fpt_distributions_MET.pdf}
+%  \caption{Methanol}\label{fig:MET_msddm_fpt_distributions}
+%  \end{subfigure}
+%  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
+%  first passage time distributions generated by 1000 realizations of the 
+%  Markov state dependent dynamical model. Note that we generated 10 times less
+%  realizations of the MSDDM which leads to noisier histograms. We show that
+%  this has a negligible effect on the fits in Figure~\ref{fig:flux_curve_sensitivity}.}\label{fig:msddm_fpt_fits}
+%  \end{figure}
 
@@
 
+%  \newpage
+%
+%  \section{Explanation of Under-Estimated MSDDM $\beta$ Values}\label{section:beta_estimates}
+%  
+%  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
+%  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
+%  Turning first to the model itself, we have designed it to ensure that the magnitude of the
+%  hops in the series of transitions between states are anti-correlated from start to finish. 
+%  This assumes that the transition correlation structure is unaffected by the
+%  sub-trajectories between each state transition. Each time a state transition occurs, one
+%  must initialize a new time series sub-trajectory with its own correlation structure. 
+%  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
+%  %in each state is relatively short making the accuracy of the correlation structure 
+%  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
+%  %$\sigma$ in trapped states. 
+%  Since we add the transitional hop lengths to each end of
+%  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
+%  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
+%  MSDDM to completely immobilize particles except when they transition between states. 
+%  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
+%  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
+%  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
+%  To generate the curves in Figure~\ref{M-fig:flux_curves_msddm}, we needed to correlate 
+%  25--1000 times more hops than for the MSD predictions in Figure~\ref{M-fig:msddm_performance}. 
+%  In short, it is computationally infeasible to use enough terms to accurately incorporate
+%  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
+%  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
+%  fractional Brownian motion, for which we have an exact simulation method, in place of 
+%  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
+%  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
+%  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
+%  of FLM.  
+%  
+%  \begin{figure}[h]
+%  \centering
+%  \begin{subfigure}{0.43\textwidth}
+%  \includegraphics[width=\textwidth]{beta_hurst.pdf}
+%  \caption{}\label{fig:beta_hurst}
+%  \end{subfigure}
+%  \begin{subfigure}{0.52\textwidth}
+%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
+%  \caption{}\label{fig:beta_parameters}
+%  \end{subfigure}
+%  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
+%  %MRS6: should try to lead with what the overall results/conclusions are.
+What does it mean that parameters are larger or smaller?
+What should the reader take from the discussion?
+Should it be in supportinig?
+%  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
+%  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
+%  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
+%  sub-trajectories between state transitions decorrelate transitional hops and because
+%  our FLM simulation procedure does not accurately correlate hops after long time lags. 
+%  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
+%  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
+%  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
+%  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
+%  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
+%  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
+%  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
+%  \end{figure}
+
   \clearpage

### 2020-01-17 Ben_Manuscripts/hdphmm/Outline.tex
Starting outline of HDP-HMM paper

--- 2019-09-04 Ben_Manuscripts/stochastic_transport/Outline.tex
@@
 
+%MRS: better to have the first outline shorter to iterate more quickly!
+%BJC1: right, this one has been in the works for a while now. Wrote the anomalous diffusion methods a long time ago
+
 %MRS: better to have a title that described a finding, rather than the
@@
 %MRS: also 'stochastic modeling' is pretty vague.  should be more precise. 
-\title{Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
+\title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
 %MRS: we should discuss whether Chris Calderon would be on this one.  I would guess no, but I don't know for sure. 
@@
 %me towards Greg Morrin who pointed me towards useful anomalous diffusion literature.
-%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
 \author{Benjamin J. Coscia \and Michael R. Shirts}
@@
   \section{Introduction}
-
-  % MRS1: I would start with something more central to the content of the paper - how do solutes move in complex separations membranes?
-Let people know right from the start what the paper is about.
-This paragraph should still be in the intro, but start with something that captures the main question of the paper.
-  % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
-  Mathematical descriptions of transport in complex separations membranes are a powerful 
-  way to understand mechanisms and formulate membrane design principles.
-  \begin{itemize}
-    \item The complexity of a model generally parallels the complexity of the 
-    transport mechanism at hand, as well as the desired outputs.
-    \item In dense homogeneous membranes, the solution-diffusion model can extract
-    diffusion and partition coefficients and has successfully predicted solute transport
-    rates.
-    \item Analogously, pore-flow models yield predictions of diffusion coefficients
-    and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
-    \item Single particle tracking allows us to further characterize more complex
-    diffusive behavior.
-    \item Finally, Molecular simulation provides a framework for studying both single
-    particle dynamics and bulk transport properties with atomic resolution.
-    \item All of these approaches facilitate speculation on the molecular origins of
-    separations and suggest experiments that should be run by attempting to give a more
-    intuitive understanding of how solutes move as a function of their environment.
-%    \item The hydrodynamic Ferry model is the simplest pore-flow model, with extensions such
-%    as the Donnan-Steric Pore Model which includes extra terms for the pressure gradient
-%    across the membrane and membrane charge.
-%    \item Dischinger et al. created an empirical correlation to determine the
-%    effect of solute physicochemical properties on solute rejection.
-  \end{itemize}
-
-%  \begin{itemize}
-%    \item More recently, rapid advancements in computational power have made it feasible
-%    to observe transport in simulated systems with atomic resolution. This allows us to
-%    shift towards analysis of the motion of individual particles and gives an even more 
-%    fundamental understanding of observed bulk properties.
-%  \end{itemize}
-
-  % BJC1: tie this paragraph into above by commenting that highly selective membranes
-  % often have complex mechanistic reasons that aren't explained by simpler models
+  %BJC: obviously this section will get beefed up
   We need highly selective membranes in order to perform efficient separations. \\
@@
   Lyotropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
-  into mechanically strong and highly selective membranes.
+  into mechanically strong membranes.
   \begin{itemize}
@@
   able to make well-converged predictions of macroscopic transport properties 
-  traditionally used to characterize membranes in the lab. \\
+  traditionally used to characterize membranes in the lab.
   \begin{itemize}
-    \item However, if we use descriptive stochastic models that sufficiently capture solute
+    \item However, if we use descriptive stochastic models that can capture solute
     dynamics, then we could project long timescale behavior in addition to gaining
@@
 
-  \noindent Researchers have developed a rigorous theoretical foundation for describing
-  the motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
+  In our previous work, we designed two different approaches which used
+  solute time series in order to parameterize stochastic models that could be used
+  to project transport on much longer timescales.
   \begin{itemize}
-    \item The tools introduced by fractional calculus are instrumental to this theory. 
-    \item They allow us to generalize the normally linear diffusion equation to fractional
-    derivative orders, providing descriptions of a much more diverse set of behavior. \cite{klages_anomalous_2008} % diverging from the relatively simple Brownian model.
-%    \item They facilitate proof of the relationship between the observed growth of a
-%    particle's mean squared displacement and underlying dwell times 
-%    \item In the absence of an external potential or complicated boundary conditions, 
-%    one can define random walk based on independent hop length and dwell time 
-%    distributions and arrive at any type of diffusive behavior. 
+  	\item Brief description of anomalous diffusion
+  	\item Brief descritpion of MSDDM
   \end{itemize}
 
-  % BJC1: moved from methods
-  \noindent Three well-known classes of behavior leading to anomalous subdiffusion are 
-  continuous time random walks (CTRW), fractional Brownian motion
-  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
+  Although both models had reasonable success at predicting solute MSDs on simulation
+  timescales, they had shortcomings.
   \begin{itemize}
-    \item The theory is frequently used to describe single particle trajectories
-    \item A CTRW is characterized by a distribution of hop lengths and 
-    dwell times, where each each hop is characterized by independent random draws from 
-    each distribution.\cite{montroll_random_1965,morrin_three_2018}
-    \item FBM is common in crowded, viscoelastic environments where each jump comes 
-    from a Gaussian distribution but is anti-correlated to its previous 
-    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
-    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
-    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
-    \item The processes described above can happen alone or in combination. 
-    \item Meroz and Sokolov suggested a decision tree for determining which subdiffusive
-    mechanisms apply to a system, adapted in Figure X. 
-    \item Of course, more complicated variations on these models can arise which we 
-    will incorporate as needed.	  % BJC1: e.g. fractional levy motion or langevin with levy noise
+  	\item Why MSDDM failed
+  	\item Why anomalous diffusion model could be better.
   \end{itemize}
 
-  % BJC1: Flow chart here
-
-  % BJC2: moved this from below
-  Our first modeling approach is based on the anomalous diffusion literature, applying the 
-  mathematical formalism describing subdiffusive transport to observed solute 
-  trajectories.
-  \begin{itemize}
-    \item We determine the most likely subdiffusive mechanisms at play using the 
-    flow chart in figure X. 
-    \item We then fit anomalous diffusion models in two ways: First, based on a
-    single set of parameters. Second, we use a two-state approach incorporating
-    two sets of parameters based on a solute's radial distance from the pore center. 
-  \end{itemize}
-
-  While elegant, pure anomalous diffusion theory may in some cases give only a qualitative
-  understanding of transport mechanisms.
-  \begin{itemize}
-    \item Complex temporal relationships in between hops may have a significant effect on the average MSD
-    \item Inhomogeneity of a medium or multiple types of interactions may lead to a number of
-    distinct diffusive regimes. 
-    \item In this case, a state based model may be useful. 
-  \end{itemize}
-
-  \noindent We can use the observations of transport from our previous work in order to create 
-  state-based models.
-  \begin{itemize}
-  	\item We know that dynamics differ between solutes moving inside the pores and 
-  	in the tails.
-  	\item We can use the anomalous diffusion approach to model our data as a 
-  	function of radial distance from the closest pore center.
-  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
-  	methods of Markov state modeling.
-  \end{itemize}
-
-  % moved parts of method to here.
-  Markov state models (MSMs) are a popular class of models used to project long timescale
-  behavior of molecules based on molecular simulation trajectories by identifying
-  different dynamical modes and quantifying the rates of transitions between them.
-  \begin{itemize}
-    \item MSMs are frequently used to study systems with slow dynamics, such as protein 
-    folding.~\cite{snow_how_2005,chodera_automatic_2007}
-    \item Researchers typically aim to come up with a low dimensional 
-    representation of the system based on features which preserve the process
-    kinetics.
-    \item This still often results in thousands of distinct states. 
-  \end{itemize}
-
-  %MRS1: probably want to make clear that you really are doing some
-  %substantially different things in in MSM modeling than most people
-  %do, by adding on modeling the z-diffusion as an auxiliary variable
-  %of the state.  I think that's actually kind of innovative.
-
-  %BJC2: moved this paragraph up from below to clarify novelty of this approach
-  Our second modeling approach adapts the MSM framework to a relatively small set
-  of known states based on the three observed solute trapping mechanisms.
-  \begin{itemize}
-    \item Standard MSMs assume first order kinetics and are typically applied 
-    towards determining equilibrium populations of various state configurations.
-    \item We extend the framework to include dynamics within states and
-    between jumps. 
-    \item That is we incorporate the magnitude and temporal dependence of the 
-    time series fluctuations between each transition to a different state. 
-    \item Temporal dependence has a significant influence on mean squared displacement.
-  \end{itemize}
-
-  In this work we attempt to model the long timescale behavior of the four 
-  fastest moving solutes studied in our previous work.
-  \begin{itemize}
-    \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
-    \item In addition to moving quickly, these solutes have a range of chemical
-    functionality and experience each of the three trapping mechanisms to different
-    degrees.
-    \item It is our goal to reproduce the MSDs exhibited by each solute on MD timescales
-    and then to project the long-term dynamics of each solute. 
-    \item We explore two modeling approaches
-%  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
-%  	learning algorithm which groups solute behavior into different dynamical states.
-  	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
-  	% require anything different in systems with more complex geometries (i.e. QI)
-  \end{itemize}
-
-  % BJC: I've been trying to understand the following justification a bit more. Does it
-  % rely on the MSD becoming linear so we can get experimentally diffusion constants? Is
-  % it just to try and reduce uncertainty in our MSD predictions? What can we learn from
-  % long stochastic simulations that we can't learn from the shorter simulations.
-  % BJC: To me the value in this is gaining a deeper mechanistic understanding by 
-  % putting things in terms of easily interpreted equations.
-  % BJC: Maybe it's just a combination of both.
-
-  % MRS: They way to think about it, I think, is that the simplest
-  % assumption is the the transport mechanism is simple diffusion;
-  % uncorrelated random jumps due to molecular collisions. If you make
-  % that assumption, you get MSD linear in time.  So that's IS a
-  % stochastic process, but not a very complex one. To make long
-  % timescale predictions, we need to increase the detail.  Is that
-  % what you are referring to? Not sure if I answered the question . . . 
-  % BJC1: Yea, I see what you're saying. Just not sure what else the long
-  % timescale will tell us that we can't learn from short ones. Probably 
-  % better to talk about this in person.
-
-%  We can use the observed mechanisms in order to choose a stochastic model of
-%  sufficient complexity One can project long timescale solute behavior by modeling transport as a
-%  stochastic process.
-%  %MRS: as above, simple diffusion is stochastic, just not very complex.  So we want to add appropriate complexity.
-%  \begin{itemize}
-%    %MRS: best talk about these mechanisms in terms of the
-%    %mathematical models they capture.  But I don't know that it's
-%    %necessary to review all of them.  
-%  
-%    %It may be a better approach to start from the features of the
-%    %problem (i.e. certain mechanisms) and choose the model (of the
-%    %existing choices) that is appropriate for those mechanisms.
-%    %I.e. diagnose first, then choose, rather than just applying a
-%    %list of models useful in other field's timeseries. Let me know if that makes sense;
-%    %I think how the methods applied are selected is a key to solve the problem.
-%
-%    \item Various disciplines study this type of problem in a number of ways.
-%    \item In the simulation literature, most start by measuring mean squared 
-%    displacement (MSD), as we did previously.  % This doesn't quite fit the thesis
-%    \item Due to the short time scales most people can feasibly simulate, the MSD 
-%    does not give a complete picture of what happens long-term, other than hinting
-%    at types of mechanisms that could lead to the curve's shape.
-%    %MRS: I'd say that MSD is too simple compared to what is going on mechanistically, but it's fundamentally the same idea.  
-%    \item mean first passage time?
-%    \item Markov state models are popular with researchers of proteins which have 
-%    many dynamical states occurring over multiple time scales.
-%    \item The anomalous diffusion literature explains the shape of MSD curves based
-%    on rigorous mathematical representations of transport mechanisms. This field is
-%    heavily used in analysis of single particle tracking experiments.
-%    \item Finally, the financial literature tackles similar problems from a more 
-%    general time series perspective. Their primary focus is towards predictions of
-%    stock market returns and volatility but their methods are widely applicable to
-%    modeling time series that exhibit a range of behavior.
-%  \end{itemize}
+  % BJC: Not sure whether to call it the infinite hidden markov model or hierarchical dirichlet process hidden markov model
+  % The former is definitely simpler.
+  In this work, we apply the infinite hidden markov model, a modeling that is agnostic
+  to the source of time series data, in order to detect and parameter an unknown number
+  of autoregressive modes.
 
@@
   atomistic molecular model of four pores in a monoclinic unit cell with 
-  10 \% water by weight. (See Figure tbd)
+  10 \% water by weight. 
   \begin{itemize}
@@
 
-  \subsection{The Anomalous Diffusion Model}\label{method:model_sFBM}
+  % BJC: can ignore this section for now. 
+  \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}  %BJC: potentially a separate paper
 
-  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
+  Hidden Markov models (HMMs) are a useful and widely used technique
+  for modeling sequences of observations where the probability of the next observation
+  in a sequence depends only on a previous unobserved, or hidden, state.~\cite{beal_infinite_2002}
   \begin{itemize}
-  %MRS: you would probably want to be clear what the mechanistic reasons for for anomalous diffusion: 
-  %want to talk about why, given the mechanisms you would consider. 
-  %BJC1: could go through flow chart
-  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
-  	does not grow linearly with time, rather it follows a power law of the form:
-	\begin{equation} 
-	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
-	\label{eqn:msd_form}
-	\end{equation} 
-	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
-	generalized diffusion coefficient.
-	\item A value of $\alpha < 1$ indicates a subdiffusive process, while values of
-	$\alpha = 1$ and $\alpha > 0$ are characteristic of Brownian and superdiffusive
-	motion respectively.
+    \item In the context of our simulations, the observations correspond to 
+    the center of mass coordinates of the solutes versus time, and the states
+    correspond to the dynamical behavior which give rise to those types
+    of observations.
+    \item Unfortunately, standard HMMs require the number of hidden states to be known
+    a priori.
+    \item One can partially overcome this by testing a range of numbers of 
+    hidden states and determining which is the best representation of their
+    data.
   \end{itemize}
 
-  \noindent We analyzed both the ensemble-averaged and time-averaged MSDs
-  of the simulated trajectories.
+  The infinite-state HMM overcomes this drawback by placing a hierarchical
+  Dirichlet process (HDP) prior on the transition probabilities.
   \begin{itemize}
-    %MRS: describe the physical situations in which one would want to choose each of these ways of calculating the MSD.
-    %BJC1: For determining ergodicity. Ensemble for determining anomalous exponent. Not sure I'll use ensemble MSD
-	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
-	position~\cite{meroz_toolbox_2015} and can be written as
+    \item Using some base probability distribution, H, a Dirichlet process 
+    (DP) generates distributions over a countably infinite number of 
+    probability measures:
     \begin{equation}
-	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle^2
-	\label{eqn:ensemble_msd}
+      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
     \end{equation}
-%	\item The average MSD calculated in this way recovers the form of
-%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
-	\item The time-averaged MSD measures the displacement between all possible time lags
-	and can be written as
+    where the $\theta_k$ are values drawn from the base distribution and the
+    weights $\beta_k$ come from a stick-breaking process parameterized by the concentration 
+    parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). 
+    \item The concentration parameter expresses one's confidence in H relative to the posterior 
+    and is closely related to the number of data observations.
+    \item Each row, $G_j$, of the transition matrix is produced by drawing from a DP specified 
+    using the $\beta$ vector as a discrete base distribution and a separate concentration
+    parameter, $\alpha$.
     \begin{equation}
-	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
+      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
     \end{equation}
-	where $\tau$ is the time lag and T is the length of the
-	trajectory~\cite{meroz_toolbox_2015}. 
+    \item This hierarchical specification ensures that the transition probabilities in 
+    each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
+    \item Once the model has converged only a finite number of states will have significant
+    sampling.
   \end{itemize}
 
-  % BJC1: moved this to intro
-%  \noindent Three common mathematical models for modeling anomalous subdiffusion
-%  processes include continuous time random walks (CTRW), fractional Brownian motion
-%  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
-%  \begin{itemize}
-%    \item FBM is common in crowded, viscoelastic environments where each step comes 
-%    from a Gaussian distribution but is anti-correlated to its previous 
-%    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
-%    \item A CTRW is characterized by a distribution of hop lengths and 
-%    dwell times, where each each step is characterized by independent random draws from 
-%    each distribution.\cite{montroll_random_1965,morrin_three_2018}
-%    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
-%    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
-%    \item The processes described above can happen alone or in combination.  	
-%  \end{itemize}
-  %MRS: talk about which of these should apply given the data mechanistically, as well as fit.
-  %BJC1: I believe that's what I try to do in the paragraph below. I can be a little more explicit
-
-  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
-  % MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
-  % BJC1: modified this paragraph to parallel the flow chart. I'm still not sure the
-  % best place for this. It seems like it belongs in the discussion, but I need to 
-  % justify the choice in model so I can write the methods about the chosen models
-  \noindent We believe that solutes in the system studied here exhibit subordinated 
-  fractional Brownian motion (sFBM) where the parent process is FBM and the 
-  leading process is a CTRW. 
+  \noindent We describe the dynamics of each state using a vector autoregressive (VAR) model. 
   \begin{itemize}
-    \item Working down the flow chart...
-  	\item We observe non-stationary $z$-coordinate traces of each solute's
-  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
-  	\item Combined with the observation that the ensemble-averaged MSD differs
-  	from the time-averaged MSD, we have evidence of non-ergodicity in this system, 
-  	a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}  % BJC: need a figure to show this
-% BJC1: following two points are weak. Linearity of CTRW doesn't necessarily hold up on short time scales.
-%  	\item For a pure CTRW, the time-averaged MSD should be linear.
-%  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
-%  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
-%  	information), which suggests that there is another underlying subdiffusive mechanism.
-	\item The process is likely subordinated to another process because the hop 
-	lengths recorded after each dwell period are anti-correlated.
-    % BJC1: need to eliminate RWF. I think a geometric argument should be convincing enough. Our
-    % system doesn't have a fractal-like structure. Monomer positions fluctuate enough that
-    % solutes can access any part of the membrane over time.
-  	\item Given the viscoelastic nature of the monomers in our system, we believe
-  	the hop lengths can be modeled with FBM. 
-  	% BJC1 : probably won't need this equation. It's really just to validate my sfbm
-  	% simulation procedure. Could go in supporting information with a plot showing that
-  	% my sims fit to t^alpha*beta
- 	\item For subordinated FBM, it can be shown that
+  	\item A VAR process is characterized by a vector of observations in a time series 
+  	that are dependent on $r$ previous values of the time series vector, weighted by a
+  	coefficient matrix $A_i$ in addition to a white noise term $\mathbf{e}_t$:
   	\begin{equation}
-  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
+  	\mathbf{y}_t = \sum_{i=1}^r A_i\mathbf{y}_{t-i} + \mathbf{e}_t~~~~\mathbf{e}_t \sim N(0, \Sigma)
   	\end{equation}
-  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
-  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
+  	\item We assumed multivariate Gaussian noise and limited our analysis to an 
+  	autoregressive order of $r=1$.
+  	\item We used a conjugate matrix-normal inverse-Wishart prior on parameters
+  	$A$ and $\Sigma$ in order to analytically draw from the posterior.
   \end{itemize}
 
-  \noindent We can characterize a CTRW process using the parameters which describe its
-  dwell time and hop length distribution.  % This is different from the emissions of the markov state model where every single step is used to construct the distribution. 
+  Based on the VAR parameters and matrix of transition probabilities, we calculated
+  the most likely sequence of hidden states.
   \begin{itemize}
-	\item We used the \texttt{ruptures} python package in order to automatically identify
-	changepoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting
-	Information for more details on chosen parameters. i.e. type of cost function, 
-	cost function penalty tolerance, number of dimensions used)
-	\item We used the corresponding hop lengths and dwell times between break points
-	to construct empirical distributions.
+    \item We repeated this process iteratively until we reached convergence % BJC: need to define convergence criteria
+    \item Our python implementation of this process is heavily adapted from the MATLAB code
+    of Fox et al.~\cite{fox_sticky_2007} 
+    \item We refer the interested reader to much more extensive descriptions of 
+    this process and its implementation. 
+    ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
   \end{itemize}
-
-  % BJC1: not sure about this anymore. Might eventually change to Levy. But in the 
-  % interest of simplicity, maybe leave it at Gaussian.
-  % BJC2: This will change to Levy. 
-  For solutes in our system, the distribution of hop lengths appears to be
-  well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
-  metzler_anomalous_2014,neusius_subdiffusion_2009}  % Note that this is different from the distribution of all increments (which is heavy-tailed)
-  \begin{itemize}
-	\item We are most interested in the standard deviation, $\sigma$, of the 
-	hop length distribution.
-  \end{itemize}
-
-  \noindent The distribution of dwell times is expected to fit a power law
-  distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
-  \begin{itemize}
-	\item Because we are limited to taking measurements at discrete values
-	dictated by the output frequency of our simulation trajectories, we fit the
-	empirical dwell times to a discrete power law distribution whose maximum
-	likelihood $\alpha$ parameter we calculated by maximizing the following
-	likelihood function: 
-        \begin{equation}
-	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
-	\beta\sum_{i=1}^{n} \text{ln}~x_i 
-	\label{eqn:powerlaw_likelihood}
-	\end{equation}
-	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
-	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
-	where $x_{min}$ is the smallest measured value of
-	$x_i$.~\cite{clauset_power-law_2009} 
-	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
-	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
-        %MRS1: can just say bootstrapping.
-  \end{itemize}
-
-  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
-  $H = \beta/2$.
-  \begin{itemize}
-  	\item Brownian motion is recovered for $H = 0.5$
-	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
-    \begin{equation}
-	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
-	\label{eqn:autocovariance}
-	\end{equation}
-	where $k$ is the number of increments between hops.
-	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
-	to the empirically measured autocovariance function.
-	\item We used statistical bootstrapping to generate a distribution of $H$ 
-	values. %BJC: can provide more detail in supporting or just reference python script
-  \end{itemize}
-
-  In general, we observe different dynamical behavior when solutes move inside the
-  pore versus in the tail region.
-  %MRS: could present the two models sequentiually.  Talk about one COULD have multiple modes, then in results present 1, then 2. 
-  \begin{itemize}
-    \item This inspired two models of varying complexity.
-    \item We created a simple, single mode model with a single $\alpha$, $\sigma$ and $H$
-    parameter fit to each solute.
-    \item Our second, two mode model assigns a set of parameters to each of 2 modes based
-    on the solute's radial location.
-    \item Solutes in mode 1 are in the pore region defined as less than 0.75 nm from any
-    pore center and all else are in mode 2, the tail region. 
-    \item We determined this cut-off and described how we calculated radial 
-    distance from the pore center in our previous work~\cite{coscia_chemically_2019}
-  \end{itemize}
-
-  For the two mode model, we needed to define a probability transition matrix 
-  describing transitions between the tail and pore region.
-
-%  We generated distributions of parameters for the dwell time and hop length
-%  distributions using statistical bootstrapping.
-%  \begin{itemize}
-%	\item For each type of distribution, we randomly selected $n$ data points from the empirical
-%	distribution with replacement.
-%	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
-%  \end{itemize}
-
-%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
-%  magnitude longer than our molecular simulations.
-  \noindent For each solute, we simulated 10000 5 $\mu$s sFBM trajectories. 
-  \begin{itemize}
-	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
-	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
-	distributions.
-	\item We propagated each trajectory until the total time equaled or exceeded 5 $\mu$s, 
-	then truncated the last data point so that the total time exactly equaled 5 $\mu$s. 
-    \item Valid comparisons are only possible between fixed length sFBM simulations. The
-    power law dwell time behavior gives rise to the aging phenomenon, embodied by
-    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
-    \item We reported the MSD after 5 $\mu$s with corresponding 95 \% intervals
-% Following probably better suited for supporting information, if included at all
-%	\item We randomly sample Gaussian hop lengths using the
-%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
-%	\item We randomly sampled dwell times from a discrete power law
-%	distribution based on the recommendations of Clauset et
-%	al.~\cite{clauset_power-law_2009}: 
-%	\begin{equation}
-%	x = \lfloor
-%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
-%	\label{eqn:discrete_powerlaw_draws}
-%	\end{equation}
-%	where $r$ is randomly drawn from a uniform distribution which we simulated
-%	with \texttt{numpy.random.uniform}.
-%	\item We found that thermal noise does not significantly influence the MSD and
-%	therefore did not add any noise to the simulated trajectories. (See supporting info)
-  \end{itemize}
-
-%BJC: probably don't need to explain this in great detail
-%  \noindent We fixed the length of each simulated trajectory so that we could compare the total
-%  MSD between different solutes without the influence of the ageing phenomenon.
-%  \begin{itemize}
-%	\item Ageing is defined by the tendency of the average MSD to decrease
-%	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
-%	\item The maximum measured dwell time can be no longer than the total length
-%	of a simulated trajectory. 
-%	\item As measurement time or trajectory length is increased, longer dwell times
-%	are incorporated into the calculation, lowering the average MSD. (See supporting
-%	info for demonstration)
-%	\item We can achieve consistent total MSDs with low uncertainty for
-%	simulated trajectories created with a given set of parameters if we fix the
-%	trajectory length (as opposed to total number of steps).  
-%  \end{itemize}
-
-  \subsection{Markov State Models}\label{method:MSMs}  
-  % BJC2: still need a better name
-  % name candidates - correlated MSMs, Dynamical mode switching
-
-  A Markov state model (MSM) decomposes a time series into a set of discrete states
-  with transitions between states defined by a transition probability matrix, T,
-  which describes the conditional probability of jumping to a specific 
-  state given the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
-  \begin{itemize}
-% BJC1: moved following to intro
-%    \item In the context of molecular simulations, MSMs are frequently used
-%    to study systems with slow dynamics, such as protein folding.~\cite{snow_how_2005,chodera_automatic_2007}
-%    \item Researchers typically aim to come up with a low dimensional 
-%    representation of the system based on features which preserve the process
-%    kinetics. This facilitates the identification of discrete states from
-%    which T is generated.
-    \item Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011}
-    and pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable 
-    of featurization and dimensional reduction.
-  \end{itemize}
-
-  In this work, we define a total of 8 discrete states based on the 3 trapping
-  mechanisms observed in our previous work. 
-  \begin{itemize}
-  	\item Therefore, there is no need to subject our trajectories to any reduction
-  	in dimensionality. 
-  	\item However, we will adopt the validation techniques used in the packages
-  	mentioned above.  
-  	%BJC: not sure the best way to lay these out
-  	\item The states we've chosen include all combinations of trapping mechanisms 
-  	in the pore and out of the pore:
-        %MRS: ``1. in tails and 5. in pores seem to encompass the things below them. Maybe us ``in tails, not trapped,'' etc. as the last entry in each column.'' 
-        %BJC2: good point
-    \begin{table}[!htb]
-	  \centering
-	  \begin{tabular}{ll}
-	  \hline
-	  1. In tails, not trapped                     & 5. In pores, not trapped                     \\
-	  2. In tails and hydrogen bonding             & 6. In pores and hydrogen bonding             \\
-	  3. In tails and associated with sodium       & 7. In pores and associated with sodium       \\
-	  4. In tails, hydrogen bonding and associated & 8. In pores, hydrogen bonding and associated \\
-	  \hline
-	  \end{tabular}
-	  \caption{}\label{table:water_content}
-   \end{table}
-%  	\begin{enumerate}
-%  	  \item Trapped in tails
-%  	  \item Trapped in tails and hydrogen bonding
-%  	  \item Trapped in tails and associated with sodium
-%  	  \item Trapped in tails, hydrogen bonding and associated
-%  	  \item In pores
-%  	  \item In pores and hydrogen bonding
-%  	  \item In pores and associated with sodium
-%  	  \item In pores, hydrogen bonding and associated
-%  	\end{enumerate}
-  	\item These choices assume that there are no significant kinetic effects resulting
-  	from solute conformational changes or pore size fluctuations, an assumption 
-  	that may be relaxed in future work.
-  \end{itemize}
-
-  % BJC: does it make sense to use Dirichlet Process as a conjugate prior for
-  % getting error on transition matrix?
-  % BJC1: aha yes! \cite{bacallado_bayesian_2009}
-
-  \noindent We constructed a state transition probability matrix based on observed solute
-  trajectories.
-  \begin{itemize}
-    \item Using methods described in our previous work, we determined 	
-    which, if any, trapping mechanisms affected the solute at each time step, and
-    assigned the observation to a specific state according to the definitions 
-    above.~\cite{coscia_chemically_2019}
-    \item Based on the current and previous state observation, we incremented the
-    appropriate entry of an $n~\times~n$ count matrix by 1, where $n$ is the number of states.
-    \item For example, if we observed state 1 followed by a transition to state 3,
-    we increment the $(1, 3)$ entry of the count matrix by 1.
-    \item We generate the transition probability matrix from the count matrix by 
-    normalizing the entries in each row so that they summed to unity.
-  \end{itemize}
-
-  \noindent We recorded the $z$-direction displacement at each time step in order to construct
-  individual emission distributions for each state and transition between states.
-  \begin{itemize}
-    \item This is where we have modified the standard MSM framework.
-    \item While the dynamics of the states themselves are important, the 
-    majority of observations involve transitions between states, so properly modeling
-    the transition dynamics is even more important.
-    \item This results in 64 distinct emission distributions. Some are far more
-    populated than others. % BJC1: need to look into lumping transition emissions into one distribution
-    %\item The shape of the distributions are symmetric and heavy-tailed. 
-  \end{itemize}
-
-  % BJC2: An abbreviated from of this paragraph probably belongs in previous section
-  % since I'll be using subordinated levy motion.
-  \noindent We modeled the emission distributions as L\'evy stable distributions.  % cauchy is a case of a Levy stable distribution. The tails are too heavy though.
-  \begin{itemize}
-    \item For independent and identically distributed (iid) random variables, the 
-    generalized central limit theorem guarantees convergence of the associated 
-    probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
-    % BJC: ``For sums of independent, iid random variables with proper normalization to the
-%    sample size, the generalized central limit theorem guarantees the convergence of
-%    the associated PDF to a L\'evy stable PDF even though the variance of these random
-%    variables diverges." \cite{klages_anomalous_2008}  % BJC: reword
-    \item The characteristic equation describing the Fourier transform of a L\'evy 
-    stable PDF is given below:
-    \begin{equation}
-    p_{\alpha, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha}|k|^{\alpha}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha)\right)\right]
-    \end{equation}
-    \item Where $\omega$ is defined with something that is complicated to format and can be 
-    added later if I keep these formulas in. % https://tex.stackexchange.com/questions/32140/how-to-write-a-function-piecewise-with-bracket-outside
-    \item $\alpha$ is the index of stability or L\'evy index, $\beta$ is the skewness 
-    parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter.
-    \item The most familiar case, and 1 of 3 that can be expressed in terms of elementary
-    functions, is the Gaussian PDF ($\alpha$ = 2).
-    \item The more general family of L\'evy stable distributions allows
-    greater flexibility in defining the observed emission distribution PDFs.
-    \item In the case that the empirical emission distributions are iid, sequential draws
-    from a L\'evy stable PDF defines a L\'evy process. 
-    \item We can relax the iid assumption and maintain the flexibility of L\'evy stable 
-    probability distributions if we instead consider the dynamics to be governed by a
-    non-Gaussian Ornstein-Uhlenbeck (OU) process.\cite{barndorffnielsen_non-gaussian_2001} % BJC: replaces Wiener process with Levy process
-    %MRS1: you many consider putting some of the long explanations in supporrting. 
-    \item OU processes contain temporal dependence but the marginal observation distributions
-    are consistent with the underlying stochastic driver.~\cite{taufer_simulation_2009}
-    \item We will discuss the implications of each.  
-    % MRS: does the process described above include the motion within the state? That is something I feel that the
-    %standard MSM doesn't include either, since they are typically interested just in the distribution of states in equilibrium, not the diffusion. 
-    % BJC1: Right, I added a sentence to the paragraph before this one to make it clear that we
-    % are adding to the standard MSM.
-  \end{itemize}
-
-  % BJC: quote from anomalous diffusion book:
-  % "While the continuous time random walk model for Levy flights ... is a
-  % conventient description, in all other cases the fraction Fokker-Planck or,
-  % equivalently, the Langevin equation with white Levy stable noise are the 
-  % description of choice" -- pretty sure this is exactly what I'm suggesting above.
-
-  L\'evy stable distributions often have heavy tails and an undefined variance 
-  which can give rise to arbitrarily long particle displacements.
-  \begin{itemize}
-  	\item We do not observe hops longer than x nm in our simulations which 
-  	emphasizes that these distributions are only an approximation.
-    \item We avoid enormous and unrealistic hops problem by truncating the tails
-    of the distribution. %BJC: can add some citations about truncated Levy distributions which are used frequently in modeling
-    \item Since solutes in our system cannot hop further than the length of our 
-    simulation unit cell, we truncate the tails of the distribution at this
-    magnitude.
-    % BJC: Is this actually the right way to do this? I am looking at unwrapped coordinates,
-    % so theoretically a particle can move as far as it wants between frames.
-    % BJC: The cut-off choice is pretty important and has a significant effect on MSD. 
-    % For example, if I truncate at the unit cell length I reproducably get a final MSD of ~ 66 nm^2 (1000 ns stochastic simulation)
-    % If I truncate the tails at double the unit cell length, I get a final MSD of ~107 nm^2
-    % The uncertainty also increases (since variance diverges for these distributions)
-    % So maybe it makes the most sense to truncate based on largest observed hops.
-    % BJC1: Okay, plan is: longest observed hop when generating realizations to match MD MSDs
-    % BJC1: Use longest expected hop based on bulk diffusion for long timescale projections.
-  \end{itemize}
-
-  We simulated realizations of the stochastic process using the probability transition
-  matrix and emission distributions.
-  \begin{itemize}
-    \item For each trajectory simulated, we chose an initial state randomly from a 
-    uniform distribution. %BJC: could construct initial distribution but I'm not sure how reliable that is based on 24 solutes that are started in the pore center.
-    \item We randomly drew subsequent state transitions and corresponding emissions 
-    from the rows of the probability transition matrix and the appropriate emission
-    distribution respectively.
-  \end{itemize}
-
-  % BJC: need to add some validation of Markovian behavior and time step choice.
-
+  \break
   \section{Results and Discussion}
 
-  \subsection{Molecular Dynamics Simulations}\label{section:MD_simulations}
-
-  The MSDs for of the solutes calculated from 5 $\mu s$ MD simulation trajectories
-  are shown in Figure TBD.
-  \begin{itemize}
-    %MRS: probably option 1.
-    \item 2 options for a figure:
-    \item 1) 2 panels: 1st panel: bar chart with final MSD value + error bars. 2nd panel: a selected MSD curve
-    \item 2) 1 panel. All MSD curves. Overlapping errors might look bad
-  \end{itemize}
-
-  %MRS: I'm not sure where the below is different from what was found in the previous study (i.e MSD's).
-  % BJC1: move to supporting if included
-%  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
-%  previous work.
-%  \begin{itemize} 
-%    \item The extent to which each trapping mechanism influences each solute is
-%  	depicted graphically in Figure TBD.
-%    \item Same types of figures from transport paper:
-%    \item Fraction participating in hydrogen bonds, fraction associated, fraction
-%    in the tails.
-%    \item Lifetimes of hbonds and sodium associations?
-%  \end{itemize}
-
-  Methanol and acetic acid are not fully equilibrated, therefore we did not use them
-  to test our models.
-
-  \subsection{Subordinated Fractional Brownian Motion Modeling}\label{section:sFBM}
-
-  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
-  of $\sigma$, $\alpha$, $H$ and $\lambda$ for each solute for the 1 and 2 mode models 
-  (see Table~\ref{table:sfbm_params}).
-  \begin{itemize}
-    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
-    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values. 
-  	\item Higher values of $\sigma$ indicate larger average hop lengths.
-  	\item Higher values of $\alpha$ mean that there will be less sampling of 
-  	long dwell times.
-  	\item Higher values of $\lambda$ truncates the power law distribution earlier
-  	preventing extremely long dwell times.
-  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
-  	of anti-correlation.
-  	\item All of which contribute to an overall increase in the MSD.
-  \end{itemize}
-
-  % BJC: this is a placeholder.
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{cccc}
-  \toprule
-  System & $\sigma$ ($nm$) & $\alpha$ & $H$ \\
-  \midrule
-  Methanol & 0.46 & 0.85 & 0.40 \\
-  Urea & 0.33 & 0.64 & 0.40 \\
-  Ethylene Glycol & 0.35 & 0.64 & 0.36 \\
-  Acetic Acid & 0.28 & 0.51 & 0.44 \\
-  \bottomrule
-  \end{tabular}
-  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
-  trajectories and then computed the average ensemble-averaged MSD of 10000 
-  simulated trajectories.}\label{table:sfbm_params}
-  \end{table}
-
-  % BJC2: Adding all combinations of distributions.
-  % Power law + Gaussian, Power law + Levy, Power law w/cutoff + Gaussian, Power Law w/cutoff + Levy
-  % BJC2: Probably a good idea to at least mention results when no anitcorrelation is included
-  \noindent We compared the MSD of simulated sFBM and sFLM trajectories to MD simulated
-  MSDs.
-  \begin{itemize}
-	\item We simulated 10000 sFBM trajectories of the same length as our MD
-	simulations, as described in Section~\ref{method:model_sFBM} of the Methods.
-	\item The final MSDs of the sFBM trajectories are compared to those 
-	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
-	\item We would like to emphasize that we rely on the MD MSD values in order to
-	define trends in the total MSD, while the sFBM trajectories and parameter 
-	values allow us to speculate as to the reasons for the observed trends. 
-%	\item There is a non-negligible amount of error in the calculation of 
-%	each parameter which prevents us from reliably portraying our sFBM MSDs as
-%	reduced	uncertainty MD MSDs.
-	% BJC: I think it's more the power law tails that increases uncertainty.
-	% BJC2: Error looks relatively small now.
-  \end{itemize}
-
-  % BJC2: A qualitative comparison of sFLM trajectories to MD trajectories might be nice.
-
-  \noindent The power law with exponential cut-off has the largest effect on the on 
-  the match between MD MSD and sFLM trajectories.
-  \begin{itemize}
-    \item Using the power law with cutoff produces predictions in relatively good agreement
-    with MD.
-  \end{itemize}
-
-  \noindent The choice between Levy and Gaussian distributions has only a small effect, 
-  but the Levy appears to fit emission distributions better.
-
-  % BJC: reduce this figure to solutes studied and put 3 bars for each solute: MD MSD, 
-  % one-mode sfbm MSD, two-mode sfbm MSD.
-  % BJC2: Actually I think I prefer showing the MSD curves on one plot, like in my research journal. Since it shows shape.
-  \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{all_emsds.pdf}
-  \caption{}\label{fig:all_msds}
-  \end{figure}
-
-  \noindent We can use the model to project our simulations out to very long timescales.
-  \begin{itemize}
-    \item We can not definitively say which combination of distributions are best to use.
-    \item Although the longest observed dwell times and hop lengths are less than
-    the length of the simulated trajectories and box lengths respectively, it is still possible
-    that that extremely long dwell times and hops are observed experimentally in rare but
-    significant cases.
-    \item We present long timescale projections using combinations of each distribution in the
-    table below
-  \end{itemize}
-
-  % BJC2: table of long timescale projections using combinations of dwell and hop distributions. 
-  %% TABLE %%
-
-  \subsection{Markov State Model Fits}\label{section:msm_results}
-  % BJC2: This section should parallel the previous section in terms of presentation of results.
-
-  We constructed emission distributions which correspond to each entry in the transition
-  matrix.
-  \begin{itemize}
-    \item Some states are sampled far more frequently than other leading to better converged
-    distributions.
-  \end{itemize}
-
-  The emission distributions are non-Gaussian and heavy-tailed (see Figure~\ref{fig:emissions_MET}).
-  \begin{itemize}
-    %\item The heavy tails of the distribution are a consequence of hopping.
-    \item Heavily sampled states fit well to L\'evy stable distributions.
-    \item The rarer states have less data, but we still assume L\'evy stable distributions.
-  \end{itemize}
-
-  % BJC: worth proving these are non-Gaussian? One might argue that they look Gaussian but they are not at all.
-  % MRS: there are some simple statistical tests for Gaussianness you can use.  Also might br good to put the 
-  % parameters with the plots, as it's hard to tell how different they may or may not be.
-  \begin{figure}[!h]
-  \includegraphics[width=\textwidth]{emissions_MET.pdf}
-  \caption{}\label{fig:emissions_MET}
-  \end{figure}
-
-  % BJC2: I need to look into the motion when a solute is trapped. It should have a very low H.
-  \noindent Motion within states is anticorrelated. 
-  \begin{itemize}
-    \item We calculated the self-similarity parameter for motion within each state.
-  \end{itemize}
-
-  \noindent The emissions resulting from transitions between states are anticorrelated.
-  \begin{itemize}
-    \item We simulated these emissions by combining all transition emissions into a single
-    distribution with a single self-similarity parameter.
-    \item We are unaware of techniques for simulating correlated draws from L\'evy distributions
-    with varying shapes.
-  \end{itemize}
-
-  % BJC2: Could explore a second model with an emission distribution for transitions in tails versus pores.
-
-  % BJC2: FIGURE: autocorrelation of motion while trapped in a state and autocorrelation of emissions.
-
-  % BJC2: This figure will show predicted MSDs versus MD MSDs
-  \begin{figure}[!h]
-  \centering
-  \includegraphics[width=0.5\textwidth]{MET_msd.pdf}
-  \caption{}\label{fig:msd_MET}
-  \end{figure}
-
-%  \noindent Anti-correlation between hops may be responsible for subdiffusive behavior.
-%  \begin{itemize}
-%    \item In general, we observe negative correlation between hops.
-%    \item A L\'evy driven OU process may be a more appropriate way to model
-%    the stochastic dynamics of this system since you can incorporate autocorrelation.
-%    \item Extracting reliable correlation functions is difficult with our data
-%    due to relatively frequent switching resulting in sets of short disjoint time 
-%    series describing each state.
-%    % \item Therefore we did not do this and attempted to fit a different model. 
-%    %BJC: we could add some artificial correlation to prove the anti-correlation hypothesis
-%  \end{itemize}
-
-  We projected the long timescale behavior using this model. 
-  %BJC2: TABLE. 
-  %BJC2: Would probably be best to combine this with table from anomalous diffusion.
-
   \section{Conclusion}
-
-  % MRS1: will want to make a stateemnt about whether these approaches
-  % are together good enough for predictive purposes, and if not,
-  % explore what else should be done in the future.
-  % BJC2: It seems like it would be hard to make say these can be used
-  % for prediction without experimental confirmation of the trends that we observe.
 
@@
   \begin{itemize}
+    \item Markov state modeling with predefined states gives a nice description
+    of transitions between observed states as well as the type of stochastic 
+    behavior shown in each state. However, it doesn't accurately portray correlated
+    time series behavior leading to overpredicted MSDs.
     \item Subordinated fractional Brownian motion has a nice theoretical foundation
@@
     consistent with MD simulated trajectories.
-    \item Markov state modeling with predefined states gives a nice description
-    of transitions between observed states as well as the type of stochastic 
-    behavior shown in each state. However, it doesn't accurately portray correlated
-    time series behavior leading to overpredicted MSDs.
   \end{itemize}

### 2020-01-19 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
comments!

@@
   the MSDs calculated from MD simulations. 
-  %BJC7: added  
-  However, qualitative differences between MD and simulated MSDDM trajectories
+  However, qualitative differences between MD and 
+  %simulated MSDDM 
+  MSDDM-generated  %MRS: abbreviation not defined first? Maybe eliminate here, just call it the Markov State dependent model
+  trajectories
   may limit its usefulness. 
-  Finally, we demonstrate how one can use our models to estimate flux of a solute
+  Finally, we demonstrate how one can use 
+  %our 
+  these 
+  models to estimate flux of a solute
   across a macroscopic-length pore and, based on those quantities, the membrane's selectivity towards each solute.
   This work helps to connect microscopic chemically-dependent solute 
-  motions and macroscopic membrane performance.
+  motions 
+  %MRS8:  Added the below, since for simple diffusion, you just calculate the diffusion constant. 
+  %and 
+  that do not follow simple diffusive behavior with 
+  macroscopic membrane performance.
 
@@
   in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
-  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
-  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
+  throughput separations. 
+  %MRS8: break sentence, tweak phrasing.
+  %however 
+  Unfortunately, aligning the microscopic hexagonal mesophases on a large 
+  scale 
+  as required for high permeability
+  has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
   Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
@@
   % eliminating the sentence.
-  %MRS6: It was also becasue they thought it was more likely to be interesting initially.  I'm in favor of 
+  %MRS6: It was also because they thought it was more likely to be interesting initially.  I'm in favor of 
   % cutting for simplicity. 
   We chose to study the H\textsubscript{II} phase because it is a simpler geometry to model than 
-  the Q\textsubscript{I} phase.  
+  the Q\textsubscript{I} phase
+  %MRS8: added as more clarification
+  and significantly more structural data is available to help ensure molecular models are consistent with experiment.
   In general, we observed subdiffusive transport behavior characterized by intermittent hops 
@@
 
+  %MRS8: really nice flow in the introduction up through here.
 %  By reducing our MD simulations to observations of several key properties that 
@@
   with nonsensical parameters has severely diminished value as it could be a 
-  consequence of overfitting.
+  consequence of over-fitting.
 
@@
   different solutes, compare the fit model parameters and relate them back to 
-  differences in solute size and chemical composition. The MSDDM characterizes 
+  differences in solute size and chemical composition. 
+  %MRS8: this may be a bit of a stretch, since it's not clear it helps that much in the end, but 
+  %is fine to leave in now - maybe we revisit if needed during revisions.
+  The MSDDM characterizes 
   explicitly defined trapping mechanisms, providing a clear picture of solute behavior
@@
   for clarity.}\label{fig:membrane_structure}
+  %MRS8: should say something about the molecular colors for (b) so it's clear what is what. 
   \end{figure}
@@
 
-  We primarily use the MSD as a tool for calculating the average properties of 
-  solute trajectories. We only compare MSDs calculated from MD simulations to 
-  those generated from our models. We do not use them to calculate diffusion 
-  constants or to relate our simulations to experimental measurements. Therefore
-  it is only important that we use a consistent definition for calculating the MSD.
-%  This approach is valid if we adhere to a consistent definition for MSD 
-%  calculations.
+  %MRS8: some tweaks
+
+  In this study, we primarily use the MSD as a tool for characterizing
+  the average dynamic behavior solute trajectories. Rather than using
+  them to calculate diffusion constants or to relate our simulations
+  to experimental measurement, we compare MSDs calculated from MD
+  simulations to those generated from our models in order to validate
+  those models. Therefore, it is only important that we use a
+  consistent definition for calculating the MSD between modeled
+  trajectories and directly observed MD trajectories.
 
@@
 
-  We chose to analyze just the time-averaged MSD because, compared to the ensemble
+  We chose to 
+  %MRS8: tweaked.
+  %analyze 
+  use 
+  just the time-averaged MSD 
+  to compare MD trajectory and modeled trajectories,
+  because, compared to the ensemble
   average, it is a more statistically robust measure of the average distance a 
@@
   trajectories we need to bound the dwell time distribution. A standard way of 
-  doing this, with easily estimated paramters, is by adding an exponential 
+  doing this, with easily estimated parameters, is by adding an exponential 
   cut-off to the power law so the dwell time distribution is now proportional 
@@
 
-  Since we also want to account for the possibility that distribution of hops is 
+  %Since 
+  Because
+  we also want to account for the possibility that distribution of hops is 
   not Gaussian, we can model them with the more general class of L\'evy stable 
@@
   hop length distributions result in rare but arbitrarily long hops. These long
-  and unrealistic hops result in over-estimated simulated MSDs. We observe that
+  and unrealistic hops result in over-estimated simulated MSDs. 
+  %MRS: could reference the figure 4 here?
+  We observe that
   the distribution of hops observed in our MD simulations are well approximated 
@@
   We simulated models with all combinations of the types of dwell and hop length
-  distributions described above, which are summarized in Table~\ref{table:anomalous_models}.
+  distributions described above, summarized in Table~\ref{table:anomalous_models}.
   All models include correlation between hops.
@@
   bootstrapping. For each bootstrap trial, we randomly chose $n$ solute trajectories,
-  where $n$ is the number of independent trajectories, with replacement from the 
+  where $n$ is the number of independent trajectories, with replacement, from the 
   ensemble of trajectories and then calculated the MSD of the subset. We reported 
@@
   %MRS6: somewhere you do talk about agreement to within 1 sigma
-  %instead of 95%, so probably should check for consistance.
+  %instead of 95%, so probably should check for consistency
 
@@
   % MRS6: suggest in the supporting information describe what measure was used to 
-  % determine that the algorithm sufficiently and reasonably approxmiates.
+  % determine that the algorithm sufficiently and reasonably approximates.
 
@@
 Should just be ``Verified the Markovianity of state transitions in MD as described in Section [X].
-Generally, how one did verification of most things can be put in supporing, since that's not central to the argument.
+Generally, how one did verification of most things can be put in supporting, since that's not central to the argument.
 ''
@@
   to construct a distribution of first passage times across a membrane pore of length $L$.
-  For computational reasons dependent on the model used, we simulated 1,000-10,000 trajectory
+  For computational 
+  %MRS8: computational costs? Clarify.
+  reasons dependent on the model used, we simulated 1,000-10,000 trajectory
   realizations, released at the pore entrance ($z=0$). In the case of 
@@
   Equation~\ref{eqn:passage_times} in order to get the MFPT.
+  %MRS8: check to make sure there is goodness-of-fit checks in the SI for fitting to the analytical model.
 
@@
 
-  The evidence suggests that solutes in this system can be well-modeled by subordinated
+  %MRS8: be more specific about which evidence. Made a stab below.   
+  %The evidence suggests
+  We find the data suggest
+  that solutes in this system can be well-modeled by subordinated
   fractional Brownian motion. In Figure~\ref{fig:solute_trajectories}, we plotted representative
@@
   \end{subfigure}
+  %MRS8: the description of hop lengths will be confusing to readers. You say it _could_ be fit by a Gaussian, but 
+  %then say that a Levy distribution fits better. So readers are not sure which one will be used in subsequent data.
   \caption{Using urea as an example, (a) the distribution of hop lengths can be fit by 
@@
   near 0. (b) The distribution of dwell times is fit well by a power law but it may 
+  %MRS8: may or does overestimate?  I would say does.
   over-estimate the probability density at long dwell times. A power law truncated with
-  an exponential cut-off may better describe the probability of long dwell times in 
+  an exponential cut-off 
+  %may better describe 
+  better describes
+  the probability of long dwell times in 
   our simulations. (c) The hops are negatively correlated to their previous hop. In
+  %MRS8: should this be _either_ fractional Brownian or Levy for clarity.
   combination, (a) -- (c) support modeling solutes as subordinated fractional Brownian
@@
   function (see Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
+  %MRS8: maybe plural, since each has an autocorrelation function.
   }\label{fig:anticorrelated_hops}
@@
   this more general fit is worthwhile. 
+  %MRS8: would it be better to put the decision here, or at least say where this decision is made?  Otherwise the reader has a lot of potential decisions to keep in their mind.
 
@@
 
-  Realizations of the AD model based on the parameterization procedures just described
-  yield qualitatively similar trajectories to those seen in our MD simulations. In
+  %MRS8: be more specific than ``the AD model'' below?
+Also, not sure how clear this thesis is since you described 2x2=4 different models in the previous two paragraphs - at this point, the reader isn't sure of a single model.
+Tried a pass.
+  %Realizations of the AD model based on the parameterization procedures just described
+  Several of the choices of AD model and parameters we have described 
+  yield qualitatively similar trajectories to those seen in our MD simulations. 
+  In
   Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for each
@@
   each solute based on the time at which the number of solutes inside the pores and tails
-  stabilized (Figure~\ref{S-fig:equilibration}). Nonetheless, we observe evidence of 
+  stabilized (Figure~\ref{S-fig:equilibration}). 
+  %MRS8: word choice?
+  %Nonetheless, 
+  With the this definition,
+  we observe evidence of 
   non-stationary solute behavior after the perceived equilibration, on the $\mu$s 
@@
 
+  %MRS: again ``the AD model'' is confusing since there are multiple models based on AD.   ``The AD approach''?
   Given stationary data, the AD model is capable of predicting solute MSDs 
@@
   equilibrated portion of the solute trajectories. Even doubling the data might 
-  not be good enough for molecules with statistical non-stationarity, so we admit that 
-  those will only be approximations.
+  not be good enough for molecules with statistical non-stationarity, 
+  %MRS8: tweak
+  %so we admit that those will only be approximations.
+  meaning the predictive and interpretive power of the time series modeling applied to these 
+  trajectories will be lower.
 
@@
 
+  %MRS8: does it make sense to say ``the AD model'', when there are several variants? 
+  %would it be better to say ``the AD approach''?
   We obtain reasonable predictions of the MD simulated MSDs when we parameterize the AD 
@@
   %BJC7: delete following sentence? I basically just said it above.  
-  Although we 
-  concluded that methanol and ethylene glycol trajectories may not yet be stationary, we 
-  include them in all analysis going forward because it is still instructive. 
+  %MRS8: yeah.
+  %Although we 
+  %concluded that methanol and ethylene glycol trajectories may not yet be stationary, we 
+  %include them in all analysis going forward because it is still instructive. 
   The MSD curves generated from the 1 and 2 mode models are overlayed with the MD 
@@
   \end{subfigure}
-  \caption{The parameters of the one mode model reveal differences in solute dynamics.
+  \caption{The parameters of the one mode model reveal differences in 
+    %MRS8: tweak
+    %solute dynamics.
+    dynamics between solutes.
   (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, and L\'evy stable, 
@@
   mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta = 0$)
-  in the L\'evy stable disributions. High values of $\sigma$ and lower values of $\alpha_h$
+  in the L\'evy stable distributions. High values of $\sigma$ and lower values of $\alpha_h$
   result in larger hops. (b) We parameterized a pure power law, $P(\alpha)$, and a 
@@
   times. Lower values of $\alpha$ lead to heavier power law tails and higher values of 
-  $\lambda$ truncate the distibution at lower dwell times. (c) Finally, we parameterized the
+  $\lambda$ truncate the distribution at lower dwell times. (c) Finally, we parameterized the
   hop autocorrelation function, $\gamma(H)$, to describe the degree of correlation between
@@
   center, otherwise they are in the tails. (a) Generally, movement is much more restricted
-  in the tail region, parameterized by lower $\sigma$ values (smaller hops) for the normal and L\'evy stable 
+  in the tail region, parameterized by lower $\sigma$ values (smaller hops) for the 
+  %MRS8: I wonder if it makes sense to be consistent between Gaussian and normal just to keep it simpler (even though synonyms)
+normal and L\'evy stable 
 distributions. Values of $\alpha_h$ are significantly lower for urea and acetic acid meaning 
@@
   the tails. Lower values of $\alpha$ correspond to power laws with heavier tails and 
-  thus higher probabilities of long dwell times. There is no easily discernable trend in
+  thus higher probabilities of long dwell times. There is no easily discernible trend in
   $\lambda$ of the truncated power law distribution. Note that we used the same Hurst parameter
@@
 
+  %MRS8: do you mean, examining up to a 1000 ns time lag (Since that what is plotted?)
   After a 1000 ns time lag, the one and two mode AD models do a fairly good job of 
@@
   %laws to describe the dwell time distributions.
+  %MRS8: maybe be a bit more explicit about which choices described above are used here. i.e. did you actually use a Gaussian  distribution because Levy was so close?
   In most cases, the sFBMcut
@@
   discussed in the previous section, long time positional anti-correlation, on
-  the order of hundreds of ns, may not exist in the MD system. Eventual loss of
+  the order of hundreds of ns, may not exist in the MD system. 
+  %MRS8: maybe there should be something here like ``as the system moves to independent parts of the pore, but this correlation does exist in the time series modeling''.
+  Eventual loss of
   correlation would result in a shift from sub-linear to linear MSD behavior. 
+  %MRS8: maybe add ``as observed in the MD trajectories.''?
   Acetic acid exemplifies this point. At first glance, acetic acid's predicted MSD appears to match the 
@@
   switch between modes the least show predicted MSDs with the greatest curvature. 
-  Due to the much larger accessible volume, methanol spends $> 90\%$ of its time
+  Due to the much larger accessible volume
+  %MRS8: added
+  that a smaller molecule has,
+  methanol spends $>90\%$ of its time
   in the hydrophobic tails (see Figure~\ref{fig:AD_mode_occupation}),
@@
   curvature. This artificially solves the problem of long timescale correlation, 
-  however we do not recommend this as it has no theoretical basis.
+  however we do not recommend this as it 
+  %MRS8: is it better to say it has no physical basis, since it doesn't reflect what is physically happening.
+  has no theoretical basis.
 
@@
   %BJC7: I'll leave it here unless we really need to cut stuff.
+  %MRS8: ``the AD model'' vs maybe ``the AD approach''
   Overall, the AD model does a reasonable job of predicting solute MSDs and its 
   parameters can help us further understand solute dynamics. Hops appear to be well
-  modeled as anti-correlated draws from Gaussian and L\'evy stable distributions. 
+  modeled as anti-correlated draws from 
+  %MRS8: maybe ``either Gaussian or Levy''?
+  Gaussian and L\'evy stable distributions. 
   The data strongly suggests that one must truncate the power law dwell time 
@@
   2 mode model. A significant amount of solute trajectory data is necessary 
-  in order to achieve good parameter estimates. The exact amount of data required 
-  is dependent on the solute studied.
+  in order to achieve good parameter estimates. 
+  %MRS8: seems kind of obvious.
+  The exact amount of data required is dependent on the solute studied.
 
@@
   %BJC5: could remove this transitional paragraph
+  %MRS8: helps flow, so probably OK.
+  %MRS8: Model vs. approach. Though the 2 state does involve some mechanistic detail (partitioning) so the below isn't quite true.
   The AD model is useful if one does not know exact transport mechanisms 
@@
 
-  Urea spends the largest fraction of its time trapped via association with sodium ions.
+  %MRS8: in section below, it would be useful to add a sentence that answers the ``so, what'' after the structural
+  %detail for each molecule - just adds reader interest.
+  Urea spends the largest fraction of its time trapped via 
+  %MRS8
+  %association 
+  associated
+  with sodium ions.
   It does so 31\% of the total time while in the tails (state 3) and 21\% of the
@@
   donors.
-
+  %MRS8: above seems incomplete - are weak h-bond donors so what?
   Ethylene glycol spends the largest fraction of its time trapped in a hydrogen
@@
   %BJC6: could delete this paragraph since described in methods
-  %MRS7: yeahm could say you created one for each solute, as described in the methods.
+  %MRS7: yeah could say you created one for each solute, as described in the methods.
   To create an MSDDM for each solute, we determined the state sequence associated
@@
   measured when solutes are hydrogen bonding and associating with sodium at the
-  same time (states 4 and 8). Motion is restricted by multiple tethers which 
+  same time (states 4 and 8). Motion is restricted by 
+  %MRS8: unclear what multiple tethers means. 
+  multiple tethers which 
   maintains a relatively narrow distribution of hop lengths.
@@
   \vspace{-1.5cm}
+  %MRS8: top figure is very confusing (also, I see a check in the urea green bar?) 
   \caption{(top) Increased anti-correlation between hops (decreased $H$) appears to 
@@
   \includegraphics[width=0.5\textwidth]{selectivity.pdf}
-  \caption{The selectivity of 2 species changes monotonically with pore length. The
+
+  \caption{The selectivity 
+    %MRS8:
+    %of 2 species 
+    between pairs of species
+    changes monotonically with pore length. The
   strength of dependence on pore length depends on the difference between $\beta$ values.
   The selectivities predicted by the sFBMcut AD model (a) are much larger in magnitude than
+  %MRS8: you removed MSDDM from figure.
   those predicted by the MSDDM (b) because predictions of the AD model result in a much
@@
   plateaus quickly which implies that a coating of LLC membrane with a thickness on the 
-  order of those already made experimentally should be sufficiently optimal.
-
+  order of those already made experimentally should be sufficiently 
+  %MRS8: optimal isn't really defined here.
+  optimal.
+
+  %MRS8: IMPORTANT POINT!
+  %MRS8: I would play up that there is absolutely no way one could figure this out 
+  %MRS8: from looking at the molecules, or the pores, or even the MD trajectories alone.
+  %MRS8: There's a lot of complex interplay here that has the potentially to really lead to interesting 
+  %MRS8: separations. Even if the models aren't quite right, they show how such selectivtiy CAN arise.
   %BJC7: I don't know why there is a big space before this paragraph when compiled
@@
   distributions for each type of transition, but this would require orders of magnitude
-  more data. This approach is further complicated by the need to make correlated draws
+  more data. 
+  %MRS8: (could add something lie below) 
+  %MRS8: or more prior assumptions about the distributions.
+  This approach is further complicated by the need to make correlated draws
   from a fractional L\'evy process with a frequently changing distribution width. 
@@
 
+  %MRS8: ``the AD model'' vs approach, since it's multiple models.
   Although the AD model generates qualitatively accurate trajectories and 
   predicts MSDs near or within the 1$\sigma$ confidence interval of our
-  MD simulations, the curvature of the predicted MSDs may not be consistent
+  MD simulations, the curvature of the predicted MSDs 
+  %MRS8: maybe ``does not appear to be consistent''?
+  may not be consistent
   with the MD simulations. The MSD curves calculated from MD simulations 
@@
   correlation to diminish on the 100 ns timescale. 
+  %MRS8: maybe add something like ``as suggested by the physical trajectories and the structural model''?
 
@@
   mechanisms. Screening a set of solutes and applying the anomalous diffusion 
+  %MRS8: I wonder if the 2 mode model can be considered a intermediate - a bit of structural information is involved.
   model can help uncover trapping mechanisms by forcing the scientist to 
@@
 % LocalWords:  urea's alkane overlayed SFLMcut underpredicted Gaussians HMM PRF
-% LocalWords:  params msddm timeseries overpredicted GAANN ACS XSEDE ACI PSC
-% LocalWords:  RMACC TOC
+% LocalWords:  params msddm timeseries overpredicted GAANN ACS XSEDE ACI PSC QI
+% LocalWords:  RMACC TOC Nanoscale Coscia lyotropic morphologies HII geens MFPT
+% LocalWords:  darvishmanesh bouchaud integrator LINCS clauset sFBMcut pyemma
+% LocalWords:  msmbuilder diffusivity Eq vt dz erfc permeabilities Kedem zoubi
+% LocalWords:  Katchalsky's nanofiltration ultrafiltration trans convective py
+% LocalWords:  bothmode todo eyetest Methanol's acid's subplots methanol's alt
+% LocalWords:  timestep pre selectivtiy foulants subfigures

### 2020-01-20 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
coments on supporting information.

@@
   \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
-  \texttt{/analysis/ markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
+  \texttt{/analysis/ Markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
   \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD or MSDDM model. \\\hline
-
+%MRS8: see main text discussion about ``the XXXX model''  
   \end{tabular}
@@
   \end{subfigure}
+  %MRS8: make clear in (b) the lines all lay on top so people don't miss it.  
   \caption{(a) The analytical autocorrelation function of FBM decays to zero faster
@@
   FLM process does not change with increasing sequence length (N). It shares the same
-  autocorrelation function as fractional Brownian motion (FBM). All sequenced used to
+  autocorrelation function as fractional Brownian motion (FBM). All 
+  %sequenced
+  sequences 
+  used to
   make this plot were generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
@@
   long hop lengths. Our distribution of hop lengths fits well to a L\'evy
-  distribution near the mean, but under samples the tails. In 
+  distribution near the mean, but under-samples the tails. In 
   Figure~\ref{fig:truncation_correction} we compare the empirically 
@@
   we slightly over sample intermediate hop lengths, and below 1 far from 
-  the center, indicating under sampling of extremely long hop lengths.
+  the center, indicating undersampling of extremely long hop lengths.
   Based on the plot, we chose a cut-off of 1 nm in order to compensate for
@@
   is near-perfect close to the mean. Intermediate hop lengths are over sampled, 
-  and the tails are under sampled. We used this type of plot to determine the
+  and the tails are undersampled. We used this type of plot to determine the
   appropriate place to truncate the L\'evy stable distributions.}\label{fig:truncation_cutoff}
@@
   different sized time steps.}\label{fig:counts}
+  %MRS: would this be clearer to see if you plotted i-j/i+j for a relative error to see how different it is from symmetric jumps? 
   \end{figure}
@@
   \caption{As the timestep between observations increases, the probability
-  transition matrix does not change signficantly.}\label{fig:transitions}
+  transition matrix does not change significantly.}\label{fig:transitions}
   \end{figure}
@@
 
-  Analagous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
+  Analogous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
   Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the
@@
   calculated from different portions of the trajectory are the same. Here we
-  plot the MSD calcluated up to a 500 ns time lag of the first and second
-  halves of the equilibrated solute trajctories. Urea and acetic acid have
+  plot the MSD calculated up to a 500 ns time lag of the first and second
+  halves of the equilibrated solute trajectories. Urea and acetic acid have
   similar MSDs, providing evidence of stationarity, while the MSDs of 
@@
   %BJC6: I think red and orange are directly on top of each other with same error bars
+  %MRS8: point out that the _cut data is the same as the data in the main tex. 
   \caption{In most cases, when using power laws with exponential cut-offs 
@@
   solute data. The models which use pure power laws systematically under-predict
-  the MD MSD curves. Over and under-estimated curvature of the of urea and acetic acid's 
+  the MD MSD curves. Over- and under-estimated curvature of the of urea and acetic acid's 
   MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
@@
   when the dwell time distributions are parameterized by a power law with an 
-  exponential cut-off. At long timescales, the MSD of Urea is under-predicted 
+  exponential cut-off. At long timescales, the MSD of urea is under-predicted 
   for both the 1 and 2 mode models with the same true of acetic acid on short 
@@
   the shape of the MSD curves. Error in the MSD curvature can also help explain some of
-  the error in the predicted MSD magnitudes. The curves predicted for Urea with both 1 
+  the error in the predicted MSD magnitudes. The curves predicted for urea with both 1 
   and 2 modes appear to have too much curvature, which causes it to under-predict the 
@@
 
-  The under-estimate of Urea's MSD at long timescales is due to long timescale
+  %MRS8: how much of this is already in the main text?  Try to limit analysis that appears in the main text.
+  The under-estimate of urea's MSD at long timescales is due to long timescale
   positional anti-correlation which may not be present in the molecularly 
@@
 
+  %MRS8: I think just ``Tables of Anomalous''.  Tabular sounds like it's a kind of anomalous diffusion.
   \section{Tabular Anomalous Diffusion Parameters}\label{section:tabular_AD_params}
 
+  %MRS8: representations of the parameters, or representations of the graphs?  Or just tabulations of the data found in the graph.
   The tables in the section are tabular representations of the parameters depicted
@@
   \end{tabular}
+  %MRS: to what extent are these captions the same as the captions to equivalent graphs main text?
+If it's the same, you probably should say so; if different, there should be some justification for the differences, and should be mentioned in the main text that more information is here.
   \caption{To create a 1 mode model for each solute, we parameterized a pure power
@@
   \newpage
-
+  %MRS8: ``Table of''. Same comments about captions being the same or different, since the data should be the same.
   \section{Tabular MSDDM parameters}\label{section:msddm_params}
@@
 
+  %MRS8: See discussion in main text on ``the AD model''
+  %MRS8: fig:msddm_fpt_fits is commented out?  Or xr not working should this be main text?
   In Figures~\ref{fig:ad_fpt_fits} and~\ref{fig:msddm_fpt_fits}, we demonstrate
@@
   \end{figure}
-
+  %MRS8: is there a way to make it easier to see the fact that the data is relatively independent of length?
+  %MRS8: Right now, you essentially have to scan between the 4 charts to see the numbers are about right. Maybe
+  %MRS8: organize it so that the 4 charts are for 4 molecules, and each chart shows plot of 
+  %MRS8: trajectory number vs pore length, so one can see that the value stays about the same except for uncertainty as 
+  %MRS8: number of trajectories changes
   % equations here 
@@
 %  MSDDM to completely immobilize particles except when they transition between states. 
-%  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
+%  Surprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
 %  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
@@
 What should the reader take from the discussion?
-Should it be in supportinig?
+Should it be in supporting?
 %  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
@@
 \end{document}
+
+% LocalWords:  LLC solutes py equispaced solute's ctrw sfbm ctrwsim MSD solute
+% LocalWords:  MSDDM XXXX GitHub plateaued Meroz Sokolov superdiffusion MSDs wt
+% LocalWords:  subdiffusion msd PR nojump xtc gro ETH nboot pdf subdiffusive xr
+% LocalWords:  RWF brownian FBM CTRWs traj npt fracshow Taqqu recentering MFPT
+% LocalWords:  Markovianity timestep GCL acf ACH bothmode params BJC tex acid's
+% LocalWords:  sFBMcut sFLMcut urea's timescale msddm fpt CDF mfpt cdf hurst
+% LocalWords:  decorrelate

### 2020-01-21 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Minor changes

@@
   allow us to predict solute MSDs. We show that both models reasonably reproduce
-  the MSDs calculated from MD simulations. 
-  However, qualitative differences between MD and 
-  %simulated MSDDM 
-  MSDDM-generated  %MRS: abbreviation not defined first? Maybe eliminate here, just call it the Markov State dependent model
-  trajectories
-  may limit its usefulness. 
-  Finally, we demonstrate how one can use 
-  %our 
-  these 
-  models to estimate flux of a solute
-  across a macroscopic-length pore and, based on those quantities, the membrane's selectivity towards each solute.
-  This work helps to connect microscopic chemically-dependent solute 
-  motions 
-  %MRS8:  Added the below, since for simple diffusion, you just calculate the diffusion constant. 
-  %and 
-  that do not follow simple diffusive behavior with 
-  macroscopic membrane performance.
+  the MSDs calculated from MD simulations. However, qualitative differences 
+  between MD and Markov state dependent model-generated trajectories may limit 
+  its usefulness. Finally, we demonstrate how one can use these models to 
+  estimate flux of a solute across a macroscopic-length pore and, based on 
+  those quantities, the membrane's selectivity towards each solute. This work 
+  helps to connect microscopic chemically-dependent solute motions that do not
+  follow simple diffusive behavior with macroscopic membrane performance.
 

### 2020-01-21 Ben_Manuscripts/stochastic_transport/cover_letter.tex
Cover letter for submission to PRE

\documentclass[fontsize=11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{hyperref}
\usepackage[export]{adjustbox}
\usepackage{anyfontsize}

\begin{document}

	\graphicspath{{./figures/}}

	%BJC: check address, phone number and fax (?) number
	\begin{figure}
	\centering
	\begin{minipage}{0.37\textwidth}
	\includegraphics[width=2.14in,left]{CUBoulder.pdf}
	\end{minipage}
	\begin{minipage}{0.62\textwidth}
	\scriptsize
	\noindent Department of Chemical and Biological Engineering \hfill t 303-735-7860~~~~~~~~~~~~~~~~~~ \\
	\noindent 596 UCB \hfill f 303-492-8425~~~~~~~~~~~~~~~~~~ \\
	\noindent Boulder, Colorado 80309 \hfill michael.shirts@colorado.edu \\
	\end{minipage}
	\end{figure}

	%\noindent May 3\textsuperscript{rd}, 2019\\
	\noindent \date

	\noindent Dear Editors,\\

	\newcommand{\ManuscriptTitle}{Capturing Subdiffusive Solute Dynamics and 
	Predicting Selectivity in Nanoscale Pores with Time Series Modeling}

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael R.
	Shirts, for	consideration for publication as a Research Article in Physical 
	Review E. We expect this work to be of significant interest to researchers 
	who study complex dynamics in both structured and amorphous soft materials.

	In this article, we use solute trajectories generated from 5$\mu$s molecular
	dynamics (MD) simulations of an inverted hexagonal (H\textsubsript{II}) phase
	self-assembled lyotropic liquid crystal (LLC) polymer membrane in order to 
	parameterize two different stochastic time series models capable of predicting
	solute flux and selectivity on a macroscopic scale. Realizations of both models
	quantitatively reproduce the mean squared displacements (MSDs) exhibited by 
	solutes in MD simulations. This is among the first studies to apply time 
	series modeling approaches in order to predict bulk materials properties.

	Recently, we characterized transport mechanisms exhibited by a series of 
	small polar solutes in an LLC Membrane (Coscia and Shirts \textit{J. Phys.
	Chem. B}, 123, 6314--6330 (2019)). We observed subdiffusive solute transport
	characterized by intermittent hops separated by periods of entrapment. In
	this work, we build on the chemical intuition gained from our previous study
	in order to formulate stochastic models which produce trajectory realizations
	that share the same dynamical properties as those exhibited by solutes in 
	our MD simulations. We explore two modeling approaches. First, based on the
	anomalous diffusion literature, we hypothesize that solutes are subject 
	to subordinated fractional Brownian or L\'evy motion. This implies that 
	solutes experience a series of dwell times separated by anti-correlated hop
	lengths. Our second approach adds state-dependent dynamics to standard Markov
	state modeling approaches. We model solute motion as a series of transitions
	between various trapped states, each with different dynamical properties.

%        Recently, we characterized an atomistic molecular model of an
%        LLC membrane that is maximally consistent with experimental
%        observations (Coscia et al. \textit{J. Phys. Chem. B}, 123,
%        289--309 (2019)). In this work, we observe and quantify
%        transport of water, sodium and 20 small polar solutes within
%        the pores of our atomistic H\textsubscript{II} phase LLC
%        membrane model. In general, all solutes exhibit subdiffusive
%        transport behavior characterized by intermittent hops between
%        long periods of entrapment. However, due the pores'
%        inhomogeneous architecture, we observed 3 different mechanisms
%        of entrapment. First, solutes can diffuse out of the pores and
%        become entangled between tails. Second, many of the solutes
%        are capable of donating hydrogen bonds to monomer head groups
%        for extended periods of time. Finally, solutes can associate
%        with monomer head group counter-ions within nanopores. Each
%        solute is influenced by each mechanism to varying degrees
%        dependent on its size and chemical functionality. We begin our
%        discussion with a broad description of these mechanisms in the
%        context of all solutes before restricting the discussion to
%        more detailed analyses of subsets of chemically-similar
%        solutes.

	%BJC: included phone numbers because it asked to do so in author's guide.
	\noindent Some suggestions for reviewers are:
	\begin{enumerate}

		\item Menachem Elimelech is a leader in the development of membrane technologies
		for	water desalination and water reuse (Yale University, 203-432-2789,
		\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).

		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
		and various	nanostructured materials (Northeastern University, 617-373-8619 	
		\href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})

		\item Mahesh Mahanthappa has experience modeling soft materials using molecular dynamics
		including work on ion transport in various ordered liquid crystalline phases. 
		(University of Minnesota, 612-625-4599,\href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})

	\end{enumerate}

	\noindent Please send correspondence regarding this paper to Michael R. Shirts (contact
	details in letterhead).\\

	\noindent Sincerely,

	\noindent Michael R. Shirts \\
	\noindent Benjamin J. Coscia \\

\end{document}

% LocalWords:  BJC

### 2020-01-23 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Incorporated MRS comments

@@
-\documentclass[aps,pre,preprint,groupedaddress]{revtex4-2}
+\documentclass[aps,pre,preprint,groupedaddress,longbibliography]{revtex4-2}
 \usepackage{CJK}
@@
 \usepackage{subcaption}
-\usepackage{caption}
+%\usepackage{caption}
 \usepackage{amsmath} % or simply amstext
@@
 \DeclareUnicodeCharacter{03C9}{$\omega$}
-\usepackage[english]{babel}
+%\usepackage[en]{babel}
 
@@
   in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
-  throughput separations. 
-  %MRS8: break sentence, tweak phrasing.
-  %however 
-  Unfortunately, aligning the microscopic hexagonal mesophases on a large 
-  scale 
-  as required for high permeability
-  has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
+  throughput separations. Unfortunately, aligning the microscopic hexagonal mesophases on 
+  a large scale as required for high permeability has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
   Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
@@
   subset of LLC monomers have been studied experimentally in membrane applications.
-  %MRS6: should these references be contracted?
-  %BJC6: probably, will see if that gets fixed by journal latex template
   \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
@@
   simulations to study the transport of 20 small polar molecules in an H\textsubscript{II}
-  phase LLC membrane.
-  %MRS6: sentence seems out of place here? True, but does it support the thesis here?
-  %BJC6: I said above how the QI phase is easier to synthesize, so I felt it necessary to 
-  % quickly justify why we studied the HII phase. Reworded to make that clearer. I'm also open to
-  % eliminating the sentence.
-  %MRS6: It was also because they thought it was more likely to be interesting initially.  I'm in favor of 
-  % cutting for simplicity. 
-  We chose to study the H\textsubscript{II} phase because it is a simpler geometry to model than 
-  the Q\textsubscript{I} phase
-  %MRS8: added as more clarification
-  and significantly more structural data is available to help ensure molecular models are consistent with experiment.
+  phase LLC membrane. We chose to study the H\textsubscript{II} phase because it is
+  a simpler geometry to model than the Q\textsubscript{I} phase and significantly more
+  structural data is available to help ensure molecular models are consistent with experiment.
   In general, we observed subdiffusive transport behavior characterized by intermittent hops 
@@
 
-  %BJC4: Added next two paragraphs to help ease more into time series modeling
   Up through our previous studies, our molecular models have provided valuable 
@@
 
-  %BJC4: 1st paragraph moved to here
   Mathematical descriptions of transport in complex separations membranes are 
@@
 
-  %BJC4: Tried to make this paragraph connect to previous a little better
   Using a bottom-up modeling approach, we can parameterize single particle behavior
@@
   correlations in solute position as well as the length of time solutes are trapped into a
-  model. We can add further
-  detail by integrating our time series analysis with our knowledge of the primary
-  trapping mechanisms as well as the solute's changing chemical environment within
-  the heterogeneous membrane.
+  model. We can add further detail by integrating our time series analysis with our 
+  knowledge of the primary trapping mechanisms as well as the solute's changing chemical
+  environment within the heterogeneous membrane.
 
@@
   substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations.
-  %MRS6: maybe rephrase the next - 'dive' is kind of casual?  Also, it seems more like the start of the next paragraph.
-  %BJC6: I just got rid of the sentence. It doesn't really add anything
-%  The formulation
-%  of these models requires a dive into stochastically driven processes.
-
-%  Our approach employs descriptive stochastic models that sufficiently
-%  capture solute dynamics are capable of projecting long timescale transport behavior in addition to gaining a deeper understanding
-%  of solute behavior on short timescales. In this work we explore two types of stochastic
-%  models parameterized by our MD simulations.
-%  
-%  Unfortunately, the timescales that we can simulate with MD are insufficient to be
-%  able to make well-converged predictions of macroscopic transport properties 
-%  traditionally used to characterize membranes in the lab.
-%  \begin{itemize}
-%    \item However, if we use descriptive stochastic models that sufficiently capture solute
-%    dynamics, then we could project long timescale behavior in addition to gaining
-%    a deeper understanding of solute behavior on short timescales.
-%  \end{itemize}
-
-  %MRS4: consider more citations below, when you talk about what researchers have done.
-  %BJC4: added citations of prominent anomalous diffusion work
-  %BJC7: changed thesis to focus more on this paper
+
   We constructed our first model by applying the rigorous theoretical foundation 
@@
 
-  %BJC4: added mention of the anomalous subdiffusion model we chose 
-%  Our first modeling approach is based on the anomalous diffusion literature, 
-%  applying the mathematical formalism describing subdiffusive transport to observed
-%  solute trajectories. Specifically, 
-  %BJC7: with changes, above thesis statement is redundant
   We treated our system as an FBM process subordinate to a CTRW, or subordinated 
@@
 
-%   is an elegant way to characterize single 
-%  particle trajectories and in addition to providing an easy and efficient way to 
-%  simulate solute trajectories, 
-%  uncover the underlying solute-membrane interactions 
-%  which result in observed transport mechanisms.
-
-  % BJC7: moved last sentence of previous paragraph to here to make it more clear that
-  % we are moving to a new model
   If one has knowledge of the primary mechanisms leading to anomalous diffusion behavior,
@@
 
-  %BJC4: making goals more explicit
   We determine the degree of success of our modeling approaches in two ways. First,
@@
 
-  % BJC4: new paragraph
   The goal of this work is not to definitively determine which modeling approach
@@
 
-%  We find that the sFBM anomalous diffusion model does the best job of reproducing
-%  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
-%  how one could predict solute flux through a theoretical pore of with an 
-%  experimentally relevant length.
-
-%  It is our goal to reproduce
-%  the mean squared displacements (MSDs) exhibited by each solute on MD timescales and
-%  then to project the long-term dynamics of each solute. We can gain further
-%  mechanistic insight by studying the parameters of each model. 
-  %BJC3: need to decide value in long term projections
-
   \section{Methods}
@@
   The appropriate scripts to use for subsequent calculations are summarized in 
-  Table~\ref{S-table:python_scripts} of the Supporting Information.
+  Table~\ref{S-table:python_scripts} of the Supplemental Material.
 
@@
   valid analyses.
-%  . Appropriate stochastic 
-%  modeling requires that solutes sample the accessible mechanisms with representative
-%  probability.
 
@@
   \centering
+  \vspace{1.1cm}
   \includegraphics[width=\textwidth]{NaGA3C11.pdf}
+  \vspace{0.6cm}
   \caption{}\label{fig:monomer_structure}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{membrane_profile.pdf}
+  \includegraphics[width=\textwidth]{membrane_profile.pdf}
   \caption{}\label{fig:membrane_profile}
@@
   used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
-  straight and uniform sized pores. Water present in the tail region is omitted 
-  for clarity.}\label{fig:membrane_structure}
-  %MRS8: should say something about the molecular colors for (b) so it's clear what is what. 
+  straight and uniform sized pores. Water molecules (red and white spheres) present in 
+  the tail region are omitted for clarity.}\label{fig:membrane_structure}
   \end{figure}
-
-%  \begin{figure}
-%  \centering
-%  \subfloat[\label{fig:monomer_structure}]{%
-%  			\includegraphics[width=0.4\textwidth, valign=c]{NaGA3C11.pdf}%
-%  			\vphantom{\includegraphics[width=0.5\textwidth, valign=c]{membrane_profile.pdf}}
-%  			}\hfill
-%  \subfloat[\label{fig:membrane_profile}]{\includegraphics[width=0.5\textwidth, valign=c]{membrane_profile.pdf}}\hfill
-%  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
-%  hexagonal phase in the presence of water where the carboxylate head groups occupy the
-%  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
-%  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
-%  straight and uniform sized pores. Water present in the tail region is omitted 
-%  for clarity.}\label{fig:membrane_structure}
-%  \end{figure}
 
@@
   for a total of 24 solutes. On the time scales which we simulate, this number
-  of solutes per pore provides a a sufficient amount of data from which to 
+  of solutes per pore provides a sufficient amount of data from which to 
   generate statistics. It also maintains a low degree of interaction between
   solutes since, at present, we are primarily interested in solute-membrane 
-  interactions.
-%  balance
-%  of a low degree of interaction between solutes, since we are primarily interested 
-%  in solute-membrane interactions at present, as well as a sufficient amount of 
-%  data from which to generate statistics on the time scales which we simulate.
-  Further details on the setup and equilibration of these systems are described in
-  our previous work.\cite{coscia_chemically_2019}
+  interactions. Further details on the setup and equilibration of these systems
+  are described in our previous work.\cite{coscia_chemically_2019}
 
@@
   in our analysis of solute kinetics. We plot the solute partition versus time in
-  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify
+  Figure~\ref{S-fig:equilibration} of the Supplemental Material in order to justify
   our choice of equilibration times for each solute.
@@
 
-  %BJC7: added following two paragraphs to clarify our usage of the MSD as a tool. Modified a bit below too  
   While it is theoretically possible to extract the value of $\alpha$ by fitting
@@
 
-  %MRS8: some tweaks
-
-  In this study, we primarily use the MSD as a tool for characterizing
-  the average dynamic behavior solute trajectories. Rather than using
-  them to calculate diffusion constants or to relate our simulations
-  to experimental measurement, we compare MSDs calculated from MD
-  simulations to those generated from our models in order to validate
-  those models. Therefore, it is only important that we use a
-  consistent definition for calculating the MSD between modeled
-  trajectories and directly observed MD trajectories.
+  In this study, we primarily use the MSD as a tool for characterizing the average
+  dynamic behavior of solute trajectories. Rather than using them to calculate 
+  diffusion constants or to relate our simulations to experimental measurement, we
+  compare MSDs calculated from MD simulations to those generated from our models 
+  in order to validate those models. Therefore, it is only important that we use a
+  consistent definition for calculating the MSD between modeled trajectories and
+  directly observed MD trajectories.
 
@@
 
-%  For a small number of solute 
-%  trajectories, this is a much more statistically robust measure of the 
-%  average distance a solute travels over time.
-
   The time averaged and ensemble averaged MSDs will give identical results 
@@
 
-  We chose to 
-  %MRS8: tweaked.
-  %analyze 
-  use 
-  just the time-averaged MSD 
-  to compare MD trajectory and modeled trajectories,
-  because, compared to the ensemble
-  average, it is a more statistically robust measure of the average distance a 
-  solute travels over time. The ensemble MSD of only 24 solute trajectories would
-  have much higher uncertainties.
-
-%  It may be difficult to calculate  ensemble
-%  MSD to estimate $\alpha$ with only 24 solute trajectories.
-%  
-%  Although theoretically possible, we do not use the 
-%  ensemble averaged MSD to calculate $\alpha$ because we can extract the same 
-%  parameter with higher precision using the dwell time distributions as described below.
+  We chose to use just the time-averaged MSD to compare MD trajectory and modeled
+  trajectories, because, compared to the ensemble average, it is a more 
+  statistically robust measure of the average distance a solute travels over time.
+  The ensemble MSD of only 24 solute trajectories would have much higher uncertainties.
 
   \subsubsection{Subordinated Fractional Brownian Motion}\label{method:sfbm}
-
-%  BJC4: I say something to the following effect in the intro
-%  The solute motion in the system studied here may be consistent with 
-%  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
-%  the leading process is a CTRW. We observe hopping and trapping which is consistent
-%  with a CTRW, along with negatively correlated hops which is consistent with FBM.
-
-%  We modeled solute motion as a continuous time random walk (CTRW) subordinate to 
-%  fractional Brownian motion, also called subordinated fractional Brownian motion (sFBM).
-%  We modeled solute motion as a CTRW subordinate to FBM, also called sFBM.
 
@@
   arbitrarily long dwell times that are never observed in MD simulations. 
-  %We cannot observe dwell times longer than the length of a single trajectory. 
   In order to directly compare our anomalous diffusion model to finite-length MD 
@@
   to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model.
-  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
-  % of the form:
-%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
-%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
-%  \label{eqn:powerlaw_cutoff}
-%  \end{equation}
   We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
@@
 
-  % BJC3: Making a logical argument regarding how we estimate H here is important
-  % because I haven't seen anyone do it this way.
   sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
@@
   and when $H > 0.5$, one observes positive correlation between hops.
-  %BJC6: I could move the following to supporting and keep last sentence.
-  %MRS7: could simplify down to saying that it's hard to estimate when H > 0.5, but you only have to deal with H < 0.5, so the difficulties are not relevant. 
-  There are many methods
-  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
-  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
-  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
+
+  There are many methods for estimating the Hurst parameter for a time series.
+  \cite{clegg_practical_2006} It can be a difficult task because 
+  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
+  $H > 0.5$, meaning one needs to study large time lags with high frequency.
   Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
   Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
-  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
+  Figure~\ref{S-fig:hurst_autocorrelation} of the Supplemental Material). Any hope of
   fitting longer time lags to our data is lost in the noise since the analytical values
@@
   Equation~\ref{eqn:fbm_autocorrelation} to the first 
-  ten  
-  0.5 ns time lags of the 
-  empirically measured autocorrelation function.
+  ten 0.5 ns time lags of the empirically measured autocorrelation function.
 
@@
 
-  %Since 
-  Because
-  we also want to account for the possibility that distribution of hops is 
+  Because we also want to account for the possibility that distribution of hops is 
   not Gaussian, we can model them with the more general class of L\'evy stable 
@@
   The characteristic equation which describes the Fourier transform of a L\'evy stable PDF is: 
-  %MRS6: maybe use just $\alpha$ for the general subdiffusive case, and alpha_h here.   
   \begin{equation}
@@
   from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
-  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
-  simulations illustrating this point.  % BJC3: could use another reference proving mathematically what I show numerically
-
-  Analogous to power law dwell times, the heavy tails of L\'evy stable 
-  hop length distributions result in rare but arbitrarily long hops. These long
-  and unrealistic hops result in over-estimated simulated MSDs. 
-  %MRS: could reference the figure 4 here?
-  We observe that
-  the distribution of hops observed in our MD simulations are well approximated 
-  by L\'evy stable distributions close to the mean, but they significantly under-sample
-  the tails. We chose to truncate the L\'evy stable distributions based
-  on where the theoretical probability distribution function (PDF) starts to 
+  See Section~\ref{S-section:H_estimate} of the Supplemental Material for numerical
+  simulations illustrating this point.
+
+  Analogous to power law dwell times, the heavy tails of L\'evy stable hop length 
+  distributions result in rare but arbitrarily long hops. These long and unrealistic
+  hops result in over-estimated simulated MSDs (see Figure~\ref{fig:ad_realizations_1mode}
+  for example). We observe that the distribution of hops observed in our MD simulations
+  are well approximated by L\'evy stable distributions close to the mean, but they 
+  significantly under-sample the tails. We chose to truncate the L\'evy stable distributions
+  based on where the theoretical probability distribution function (PDF) starts to 
   deviate from the empirically measured PDF (see Section~\ref{S-section:truncation}
-  of the Supporting Information).~\cite{mantegna_stochastic_1994}
+  of the Supplemental Material).~\cite{mantegna_stochastic_1994}
 
@@
   We populated a 2$\times$2 count matrix by incrementing the appropriate entry by 1 
-  each time step 
-% For example, if we observed the solute in the tails followed by a transition to 
-% the pores, we incremented the $(2, 1)$ entry of the count matrix by 1.
-% We generated
-  and then generated a transition probability matrix by normalizing the entries
-  in each row of the count matrix so that they summed to unity.
+  each time step and then generated a transition probability matrix by normalizing 
+  the entries in each row of the count matrix so that they summed to unity.
 
@@
 
+%BJC8: from author guidelines. Should there only be a line between column headings?
+%Use a single horizontal rule to separate the column headings from the entries in the table.
+Use horizontal space within the body of the table to separate broad groups of entries.
+Extra vertical space may be used between columns.
+Avoid vertical rules in tables.
+Use lower-case roman letters for footnotes placed at the bottom of a table.
+
   \begin{table}[!htb]
 	  \centering
-	  \begin{tabular}{|c|c|c|}
-	  \hline
-	  Dwell Distribution                & Hop Length Distribution & Abbreviation \\
+	  \begin{tabular}{ccc}
+	  %\hline
+	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
 	  \hline
@@
       Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
-	  \hline
+	  %\hline
 	  \end{tabular}
-	  \caption{We tested models with various modifications to the dwell and hop
-	  length distributions. We incorporate correlation structure into all models.}\label{table:anomalous_models}
+	  \caption{We tested four anomalous diffusion models with various modifications 
+	  to the dwell and hop length distributions. We incorporate correlation structure
+	  into all models.}\label{table:anomalous_models}
  \end{table}
 
-  % BJC3: will need to modify this text to reflect different lengths of simulations
   For each solute, we simulated 1,000 anomalous diffusion trajectories of length
@@
 
-  %BJC6: added this. Not sure how much detail is necessary
-  %MRS7: seems fine.
   We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
@@
   intervals.
-  %MRS6: somewhere you do talk about agreement to within 1 sigma
-  %instead of 95%, so probably should check for consistency
 
@@
   the transition probabilities from a finite data set, they have an associated 
-  uncertainty which we 
-  %MRS4: not quite sure what you mean by incorporating uncertainty. 
-  %BJC4: Added comment about having a finite amount of data with which to create transition matrix. Therefore it is uncertain
-  incorporated by re-sampling each row from a two dimensional Dirichlet distribution
-  (which is also a beta distribution for the 2D case) with concentration parameters 
-  defined by the count matrix.~\cite{bacallado_bayesian_2009}
+  uncertainty which we incorporated by re-sampling each row from a two dimensional
+  Dirichlet distribution (which is also a beta distribution for the 2D case) with 
+  concentration parameters defined by the count matrix.~\cite{bacallado_bayesian_2009}
 
@@
   added an empirical correction to enhance the accuracy of the correlation structure
-  (see Section~\ref{S-section:flm_correlation} of the Supporting Information for 
+  (see Section~\ref{S-section:flm_correlation} of the Supplemental Material for 
   validation of the approach).
-  % MRS6: suggest in the supporting information describe what measure was used to 
-  % determine that the algorithm sufficiently and reasonably approximates.
-
-%  When simulating 5 $\mu s$ FLM trajectories, we limited the maximum hop length to
-%  be no larger than the largest hop observed in our MD simulations. L\'evy stable 
-%  distributions often have heavy tails and an undefined variance which can give 
-%  rise to arbitrarily long particle displacements. We do not observe hops longer 
-%  than x nm in our simulations which emphasizes that these distributions are only 
-%  an approximation. We avoid enormous and unrealistic hops problem by truncating 
-%  the tails of the distribution.
-
-%  An important feature 
-%  of L\'evy distributions is their heavy tails. Generally, a lower L\'evy index is 
-%  characteristic of heavier tails, meaning higher probabilities of extremely large jumps.
-%  In practical applications these extremely large hop lengths are unrealistic, especially
-%  when comparing to MD.
-
-%  BJC4: I already said this above
-%  When simulating MD-length FLM trajectories, we limited the maximum hop length based on where
-%  the empirical hop distribution began to significantly under-sample the theoretical
-%  maximum likelihood estimate (MLE) L\'evy stable distribution (see 
-%  Section~\ref{S-section:truncation} of the Supporting Information).
-
-%  For our 1 second simulations, we limited the maximum hop length to that seen by
-%  the same solute undergoing Brownian motion in an unconfined aqueous environment. 
-%  We have no reason to believe there is any kind of facilitated diffusion, so 
-%  excursions characteristic of Brownian motion represent a reasonable upper limit
-%  on hop lengths. To determine these limits we placed 24 solutes in a cubic box of 
-%  water, 4 nm on each side. We allowed the solutes to diffuse for 100 ns, more than
-%  ensuring the mean squared displacement entered a linear regime. We recorded the largest
-%  observed hop length over a 0.5 ns time lag.
 
@@
 
+  %BJC8: reformatted. I think this is what they want in terms of format
   \begin{table}[!htb]
 	  \centering
-	  \begin{tabular}{|l|l|}
+	  \begin{tabular}{ll}
+	  \multicolumn{2}{c}{Markov State-Dependent Dynamical Model State Definitions} \\
 	  \hline
@@
 	  3. In tails and associated with sodium        & 7. In pores and associated with sodium       \\
-	  4. In tails, hydrogen bonding and associated & 8. In pores, hydrogen bonding and associated \\
-	  \hline
+	  4. In tails, hydrogen bonding and associated  ~~~~& 8. In pores, hydrogen bonding and associated \\
+	  %\hline
 	  \end{tabular}
@@
 	  trapping mechanisms.}\label{table:states}  
-	  %BJC3: the caption will depend on the journal. I don't
-	  % like that J Phys Chem B forces the captions as titles, but if we choose them I think it would
-	  % be cleaner to make the caption more title-like.
   \end{table}
@@
   verified the Markovianity of state transitions as described in 
-  Section~\ref{S-section:markov_validation} of the Supporting Information.
-
-  %BJC6: could defer most of this to supporting.  
-  %MRS7: yeah, supporting.
-Should just be ``Verified the Markovianity of state transitions in MD as described in Section [X].
-Generally, how one did verification of most things can be put in supporting, since that's not central to the argument.
-''
-%  We verified the Markovianity of state transitions by solutes in our MD simulations 
-%  by analyzing the empirically measured transition matrix. An important condition
-%  of a Markov process is the satisfaction of detailed balance:
-%  \begin{equation}
-%  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
-%  \end{equation}
-%  where $P$ is the equilibrium distribution of states. In other words, the number of
-%  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
-%  test is to verify that $T$ holds up to coarser time scale partitioning. As long as solutes
-%  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
-%  with time.~\cite{swope_describing_2004} We verified these properties 
-%  in Section~\ref{S-section:markov_validation} of the Supporting Information.
+  Section~\ref{S-section:markov_validation} of the Supplemental Material.
 
@@
   distributions from 64 to 9 (1 for each of the 8 states and 1 for transitions between states).
-
-%  We observed negatively correlated hops within each state and among transitions between
-%  states. We can use the Hurst parameter to describe this negative time series correlation
-%  however, there is not sufficient data to accurately measure a Hurst parameter for 
-%  each type of transition. We avoided this problem by treating transitions as correlated
-%  emissions from a single L\'evy stable distribution. This reduces the number of emission
-%  distributions from 64 to 9 (1 for each state and 1 for transitions between states).
 
@@
 
-%  corresponding emissions from the rows of the probability transition matrix and the 
-%  appropriate emission distribution respectively. We added correlation between transitions
-%  as well as to sequences of emissions while dwelling in specific states using the FLM
-%  simulation procedure described in Section~\ref{method:model_sFBM}.
-
   \subsection{Estimating Solute Flux}\label{method:mfpt}
@@
   to construct a distribution of first passage times across a membrane pore of length $L$.
-  For computational 
-  %MRS8: computational costs? Clarify.
-  reasons dependent on the model used, we simulated 1,000-10,000 trajectory
-  realizations, released at the pore entrance ($z=0$). In the case of 
-  uncorrelated hops, one can continuously draw from the hop length distribution until 
-  $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
+  For each pore length, we simulated 10,000 realizations of the AD model
+  % and, due to 
+  %computational costs, 1,000 realizations of the MSDDM, 
+  all released at the pore entrance ($z=0$).
+  In the case of uncorrelated hops, one can continuously draw from the hop length 
+  distribution until $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
   between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
@@
   which traverses from $0$ to $L$ without becoming negative.
-  %BJC4: below is only necessary if you the mean of the distribution exists.
-  %It is important to choose a value of $n$ sufficiently
-  %large that all trajectories reach $L$, or else the mean first passage time will 
-  %be underestimated.
 
@@
   possible that a very long passage time has been excluded from the distribution.
-
-  %BJC4: can probably delete this paragraph
-%  We are unaware of an analytical passage time distribution which describes our 
-%  geometry. The setup of our system is consistent with a one dimensional interval 
-%  with two absorbing boundaries. In the absence of an external force and with a constant
-%  diffusion coefficient, $D$, the MFPT is simply:
-%  \begin{equation}
-%  T = \frac{z_0(L - z_0)}{2D}
-%  \end{equation}
-%  where $z_0$ is the initial position of particle trajectories.~\cite{gitterman_mean_2000}
-%  Of course that implies a conventional MFPT of 0 since particles overwhelmingly exit the
-%  pore at $z=0$. Therefore, we chose only to include trajectories in the MFPT calculation 
-%  which cross the boundary at $L$. We are unaware of an analytical form of the MFPT or 
-%  the distribution of passage times describing our system even in the simplest case of 
-%  Brownian increments. %BJC4: still digging for an analytical solution. Rich said the 
-%  %'marathon' runner problem might give a solution. It may be the same as the distribution
-%  % of runners crossing the finish line
 
@@
   of Equation~\ref{eqn:passage_times} is given in Section~\ref{S-section:fpt_derivation}
-  of the Supporting Information. We calculated the expected value of 
+  of the Supplemental Material. We calculated the expected value of 
   Equation~\ref{eqn:passage_times} in order to get the MFPT.
   %MRS8: check to make sure there is goodness-of-fit checks in the SI for fitting to the analytical model.
-
-  %MRS5: I would put this next section up until just before Eq. 15 in the supporting information (keep any citations in the main text). 
-  %BJC5: moved to supporting
-%  To derive an analytical equation, first consider an initial pulse spreading out 
-%  over time with a fixed mean. We can solve for the time-dependent probability density
-%  of particle positions by solving the one dimensional diffusion equation:
-%  \begin{equation}
-%  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
-%  \end{equation}
-%  The appropriate initial and boundary conditions are:
-%  $$BC1: t > 0, z = \infty, p = 0$$
-%  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
-%  $$IC: t = 0, c = M\delta(z)$$
-%  where $M$ is the total number of particles in the system. It has been shown 
-%  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
-%  \begin{equation}
-%  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
-%  \end{equation}
-%  We can make the substitution $z = z - vt$, where $v$ represents a constant average
-%  velocity, in order to linearly shift the mean as a function of time:
-%  \begin{equation}
-%  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
-%  \end{equation}
-%  One can track the fraction of particles, $F$, that have crossed the pore 
-%  boundary by integrating:
-%  \begin{equation}
-%  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
-%  \end{equation}
-%  where $L$ is the pore length. This represents the cumulative first passage 
-%  time distribution so we take its derivative in order to arrive at the first
-%  passage time distribution:
 
@@
 
-  %MRS8: be more specific about which evidence. Made a stab below.   
-  %The evidence suggests
-  We find the data suggest
-  that solutes in this system can be well-modeled by subordinated
-  fractional Brownian motion. In Figure~\ref{fig:solute_trajectories}, we plotted representative
-  trajectories for each solute. They are characterized by intermittent hops between
-  periods of entrapment. The near-Gaussian distribution of jump lengths and power law 
-  distribution of dwell times are both characteristic of CTRWs 
-  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
-  anti-correlation between hops suggests a fractional diffusion process is subordinate 
-  to the CTRW. Of the different models, a process subordinated by FBM or FLM is best 
-  supported by the data because the analytical correlation structures of hop lengths are
-  close to those observed in our simulations (Figure~\ref{fig:hop_acf}). Fractional 
-  motion is common in crowded viscoelastic environments where movement is highly 
-  influenced by the movement of surrounding components, such as monomer tails in our 
-  case.~\cite{ernst_fractional_2012}
+  We find the data suggests that solute motion in this system can be well-modeled by 
+  subordinated fractional Brownian motion. In Figure~\ref{fig:solute_trajectories},
+  we plotted representative trajectories for each solute. They are characterized 
+  by intermittent hops between periods of entrapment. The near-Gaussian distribution
+  of jump lengths and power law distribution of dwell times are both characteristic
+  of CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). 
+  The apparent anti-correlation between hops suggests a fractional diffusion process
+  is subordinate to the CTRW. Of the different models, a process subordinated by FBM
+  or FLM is best supported by the data because the analytical correlation structures
+  of hop lengths are close to those observed in our simulations (Figure~\ref{fig:hop_acf}).
+  Fractional motion is common in crowded viscoelastic environments where movement is
+  highly influenced by the movement of surrounding components, such as monomer tails 
+  in our case.~\cite{ernst_fractional_2012}
 
@@
   \end{subfigure}
-  %MRS8: the description of hop lengths will be confusing to readers. You say it _could_ be fit by a Gaussian, but 
-  %then say that a Levy distribution fits better. So readers are not sure which one will be used in subsequent data.
   \caption{Using urea as an example, (a) the distribution of hop lengths can be fit by 
@@
   distribution does a better job of capturing the heavier tails and increased density
-  near 0. (b) The distribution of dwell times is fit well by a power law but it may 
-  %MRS8: may or does overestimate?  I would say does.
-  over-estimate the probability density at long dwell times. A power law truncated with
-  an exponential cut-off 
-  %may better describe 
-  better describes
-  the probability of long dwell times in 
+  near 0. We explore models fit to both distributions since Gaussian hops are convenient to
+  model. (b) The distribution of dwell times is fit well by a power law but it
+  over-estimates the probability density at long dwell times. A power law truncated with
+  an exponential cut-off better describes the probability of long dwell times in 
   our simulations. (c) The hops are negatively correlated to their previous hop. In
-  %MRS8: should this be _either_ fractional Brownian or Levy for clarity.
-  combination, (a) -- (c) support modeling solutes as subordinated fractional Brownian
-  and L\'evy motion. All other solutes show similar distributions and autocorrelation
-  function (see Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
-  %MRS8: maybe plural, since each has an autocorrelation function.
+  combination, (a) -- (c) support modeling solutes as either subordinated fractional
+  Brownian or L\'evy motion. All other solutes show similar distributions and autocorrelation
+  functions (see Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
   }\label{fig:anticorrelated_hops}
@@
   length distribution. However, since there are no known exact simulation techniques
-  for generating realizations of fractional L\'evy motion, we must evaluate whether
-  this more general fit is worthwhile. 
+  for generating realizations of fractional L\'evy motion, this more general 
+  fit may not be worthwhile. In fact, we typically observe very little difference 
+  between model predictions parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).
+%  we must evaluate whether
+%  this more general fit is worthwhile. 
   %MRS8: would it be better to put the decision here, or at least say where this decision is made?  Otherwise the reader has a lot of potential decisions to keep in their mind. 
+  %BJC8: probably a good idea.
 
@@
   %Realizations of the AD model based on the parameterization procedures just described
-  Several of the choices of AD model and parameters we have described 
-  yield qualitatively similar trajectories to those seen in our MD simulations. 
-  In
-  Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for each
+  Several of the choices of AD models and parameters we have described yield 
+  qualitatively similar trajectories to those seen in our MD simulations. 
+  In Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for each
   combination of the dwell time and hop distribution, labeled according to Table~\ref{table:anomalous_models}.
@@
   made with these models consistently under-predict the MD MSDs (see 
-  Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supporting Information). Therefore, 
+  Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supplemental Material). Therefore, 
   we will not include the pure sFBM or sFLM models in the remainder of our analysis.
-
-%  \begin{figure}
-%  \centering
-%  %plot_ad_realization.py
-%  \includegraphics[width=0.5\textwidth]{ad_realizations_1mode.pdf}
-%  \caption{Simulations of 1 mode AD model trajectories for urea display qualitatively
-%  similar hopping and trapping behavior to that shown in Figure~\ref{fig:solute_trajectories}. 
-%  Dwell times appear exaggerated in the sFBM and sFLM models because the power law dwell
-%  time distributions are not truncated and have infinite variance.
-%  %Analogous plots are shown for other solutes
-%  %MRS6: I don't think the comparison between the cut and no cut are that interesting for the main text.  Move to supporting?
-%  %MRS6: comparisons between modeled and actual trajectories side by side would be more interesting. 
-%  %BJC5: todo: add plots to SI. Show I add a 2 mode model plot?
-%  %and the 2 mode model in the Supporting Information. 
-%  }\label{fig:ad_eyetest}
-%  \end{figure}
 
@@
   stabilized (Figure~\ref{S-fig:equilibration}).  
-  %MRS8: word choice?
-  %Nonetheless, 
-  With the this definition,
-  we observe evidence of 
-  non-stationary solute behavior after the perceived equilibration, on the $\mu$s 
-  timescale. In Table~\ref{table:stationarity}, we compare the MSD of the solutes 
-  calculated using trajectory data from the first and second halves of the 
-  ``equilibrated" simulation time. Ethylene glycol and methanol show considerable 
-  differences between the MSDs of the two halves. Urea and acetic acid appear to demonstrate satisfactory
-  stationarity. The shapes of their MSD curves are also very similar (see 
-  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
+  With this definition, we observe evidence of non-stationary solute behavior after 
+  the perceived equilibration point, on the $\mu$s timescale. In Table~\ref{table:stationarity},
+  we compare the MSD of the solutes calculated using trajectory data from the first and
+  second halves of the ``equilibrated" simulation time. Ethylene glycol and methanol show
+  considerable differences between the MSDs of the two halves. Urea and acetic acid appear
+  to demonstrate satisfactory stationarity. The shapes of their MSD curves are also very 
+  similar (see Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).
 
@@
 
-  %MRS: again ``the AD model'' is confusing since there are multiple models based on AD.   ``The AD approach''?
-  Given stationary data, the AD model is capable of predicting solute MSDs 
+  Given stationary data, the AD approach is capable of predicting solute MSDs 
   measured from MD simulations within or near statistical uncertainty.
-  In Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized 
-  the AD model using the first half of the stationary solute equilibrated trajectories 
+  In Figure~\ref{S-fig:train_test} of the Supplemental Material, we parameterized 
+  the AD models using the first half of the stationary solute equilibrated trajectories 
   and then compared the model predictions to the MD MSD of the second of half 
@@
   equilibrated portion of the solute trajectories. Even doubling the data might 
-  not be good enough for molecules with statistical non-stationarity, 
-  %MRS8: tweak
-  %so we admit that those will only be approximations.
-  meaning the predictive and interpretive power of the time series modeling applied to these 
+  not be good enough for molecules with statistical non-stationarity, meaning the
+  predictive and interpretive power of the time series modeling applied to these 
   trajectories will be lower.
-
-%  In most cases, 
-%  the magnitude of the MSD predictions after a 
-%  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
-%  sFLMcut), but still appear to systematically under-predict the mean.  Longer simulations and more independent trajectories may
-%  be necessary.
-
-  %BJC: say something about how more independent trajectories may not fix the problem
-  % because there are different features of the MSD curves on different timescales.
 
@@
   %would it be better to say ``the AD approach''?
-  We obtain reasonable predictions of the MD simulated MSDs when we parameterize the AD 
-  model with all available data after the perceived equilibration time. 
-  %BJC7: delete following sentence? I basically just said it above.  
-  %MRS8: yeah.
-  %Although we 
-  %concluded that methanol and ethylene glycol trajectories may not yet be stationary, we 
-  %include them in all analysis going forward because it is still instructive. 
+  We obtain reasonable predictions of the MD simulated MSDs when we parameterize AD 
+  models with all available data after the perceived equilibration time.  
   The MSD curves generated from the 1 and 2 mode models are overlayed with the MD 
@@
   \end{subfigure}
-  \caption{The parameters of the one mode model reveal differences in 
-    %MRS8: tweak
-    %solute dynamics.
-    dynamics between solutes.
-  (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, and L\'evy stable, 
+  \caption{The parameters of the one mode model reveal differences in dynamics between
+  solutes. (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, and L\'evy stable, 
   $L(\sigma, \alpha_h)$, distributions to describe solute hop lengths. We assume the 
@@
   in the tail region, parameterized by lower $\sigma$ values (smaller hops) for the 
-  %MRS8: I wonder if it makes sense to be consistent between Gaussian and normal just to keep it simpler (even though synonyms)
-normal and L\'evy stable 
-distributions. Values of $\alpha_h$ are significantly lower for urea and acetic acid meaning 
+  Gaussian and L\'evy stable distributions. Values of $\alpha_h$ are significantly lower for urea and acetic acid meaning 
   there is a larger probability that they will take large hops. (b) Dwell times are longer in 
@@
 
-  %MRS8: do you mean, examining up to a 1000 ns time lag (Since that what is plotted?)
-  After a 1000 ns time lag, the one and two mode AD models do a fairly good job of 
-  predicting the magnitude of the MD MSD curves.
+  The one and two mode AD models do a fairly good job of predicting the magnitude of 
+  the MD MSD curves examined up to a 1000 ns time lag.
   % when we use truncated power
@@
   %MRS8: maybe be a bit more explicit about which choices described above are used here. i.e. did you actually use a Gaussian  distribution because Levy was so close?
-  In most cases, the sFBMcut
-  and sFLMcut models give very similar results, most likely because their $\alpha_h$
-  parameter values are relatively close to 2, meaning the hop length distributions
-  are nearly Gaussian even when fit to a more general L\'evy distribution.
+  %BJC8: I thought that sFBMcut and sFLMcut implied which distributions I used. It's in Table I
+  In most cases, the sFBMcut and sFLMcut models give very similar results, most 
+  likely because their $\alpha_h$ parameter values are relatively close to 2, meaning
+  the hop length distributions are nearly Gaussian even when fit to a more general 
+  L\'evy distribution.
 
@@
   %MRS8: maybe there should be something here like ``as the system moves to independent parts of the pore, but this correlation does exist in the time series modeling''.
-  Eventual loss of
-  correlation would result in a shift from sub-linear to linear MSD behavior. 
-  %MRS8: maybe add ``as observed in the MD trajectories.''?
-  Acetic acid exemplifies this point. At first glance, acetic acid's predicted MSD appears to match the 
-  curvature of MD quite well, but closer examination reveals that the MD MSD 
-  curve actually shifts from a sub-linear to a linear regime around 500 ns.
+  Eventual loss of correlation would result in a shift from sub-linear to linear 
+  MSD behavior, as observed in the MD trajectories. Acetic acid exemplifies this point.
+  At first glance, acetic acid's predicted MSD appears to match the curvature of MD 
+  quite well, but closer examination reveals that the MD MSD curve actually shifts
+  from a sub-linear to a linear regime around 500 ns.
 
@@
   switch between modes the least show predicted MSDs with the greatest curvature. 
-  Due to the much larger accessible volume
-  %MRS8: added
-  that a smaller molecule has,
-  methanol spends $>90\%$ of its time
-  in the hydrophobic tails (see Figure~\ref{fig:AD_mode_occupation}),
+  Due to the much larger accessible volume that a smaller molecule has, methanol 
+  spends $>90\%$ of its time in the hydrophobic tails (see Figure~\ref{fig:AD_mode_occupation}),
   so mode transitions are relatively rare and the predicted MSDs have significant 
   curvature. This artificially solves the problem of long timescale correlation, 
-  however we do not recommend this as it 
-  %MRS8: is it better to say it has no physical basis, since it doesn't reflect what is physically happening.
-  has no theoretical basis.
+  however we do not recommend this as it has no physical basis.
 
@@
   behavior that help explain the difference between the MSDs of different solutes. 
-  %BJC6: need to double check this after alpha_h c parameter simulations are re-done
   Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
@@
   limit of 0.5 indicate a lower degree of negative correlation between hops. All 
-  of these changes in physical behavior contribute to 
-  %MRS6: increase in the MSD compared to what, be specific?
-  %BJC6: made more specific
-  an overall increase in the predicted MSD.
-  % and can be correlated to physical behavior 
-  %that explains differences in the MD MSDs.
+  of these changes in physical behavior contribute to an overall increase in the 
+  predicted MSD.
 
@@
 
-  %BJC6: Could delete this paragraph or move an abridged version to conclusions
-  %MRS7: Good question.  Seemed OK when I was reading it. Summarizing what was found in this section.
-  %BJC7: I'll leave it here unless we really need to cut stuff.
-  %MRS8: ``the AD model'' vs maybe ``the AD approach''
-  Overall, the AD model does a reasonable job of predicting solute MSDs and its 
+  Overall, the AD approach does a reasonable job of predicting solute MSDs and its 
   parameters can help us further understand solute dynamics. Hops appear to be well
-  modeled as anti-correlated draws from 
-  %MRS8: maybe ``either Gaussian or Levy''?
-  Gaussian and L\'evy stable distributions. 
+  modeled as anti-correlated draws from either Gaussian or L\'evy stable distributions. 
   The data strongly suggests that one must truncate the power law dwell time 
@@
   %MRS8: seems kind of obvious.
-  The exact amount of data required is dependent on the solute studied.
+%  The exact amount of data required is dependent on the solute studied.
 
@@
   independent of which region they are in. 
+  %BJC8: added following sentence  
+  We can relate these interactions to solute chemical functionality and use that intuition
+  to hypothesize new designs for LLC monomers which control the transport rate of specific
+  solutes.
 
@@
   %detail for each molecule - just adds reader interest.
-  Urea spends the largest fraction of its time trapped via 
-  %MRS8
-  %association 
-  associated
-  with sodium ions.
+  %BJC8: I'm interpreting this as, "how does this information relate to design"
+  Urea spends the largest fraction of its time trapped via association with sodium ions.
   It does so 31\% of the total time while in the tails (state 3) and 21\% of the
@@
   donors. 
+  %BJC8: something like this I think.   
+  Therefore the transport rate of urea may be enhanced the most by removing or changing 
+  the counter-ion identity.
   %MRS8: above seems incomplete - are weak h-bond donors so what?
+
   Ethylene glycol spends the largest fraction of its time trapped in a hydrogen
@@
   head groups and the ether linkages between the head groups and monomer tails.
+  %BJC8: added following sentence
+  The transport rate of ethylene glycol might be increased by removing hydrogen 
+  bond accepting groups from the LLC monomers, especially those which stabilize
+  the solute in the tails (i.e. the ether linkages).
 
   Methanol spends most of its time unbound in the tail region (state 1) and spends a 
-  significant portion of time hydrogen bonded while in the tail regions.
+  significant portion of time hydrogen bonded while in the tail region.
   Tail region hydrogen bonds are donated from methanol to the ether linkages between
   the monomer head groups and tails. 
+  %BJC8: added  
+  If one desires an increased methanol transport 
+  rate, the LLC system may benefit most by preventing its partition into the monomer
+  tails. This might be achieved by adding cross-linkable groups near the monomer
+  head groups.
 
@@
   weaker interaction than hydrogen bonding. 
+  %BJC8:added  
+  As with ethylene glycol, one might increase
+  the transport rate of acetic acid by removing hydrogen bond accepting constituents
+  of the LLC monomer. With this modification, we hypothesize that acetic acid would 
+  show similar transport rates to urea given their structural similarity.
 
@@
 
-  %BJC6: could delete this paragraph since described in methods
-  %MRS7: yeah could say you created one for each solute, as described in the methods.
   To create an MSDDM for each solute, we determined the state sequence associated
@@
   fit well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
-  solutes in Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The 
+  solutes in Figure~\ref{S-fig:ad_fpt_fits} of the Supplemental Material. (b) The 
   single particle flux measured by the sFBMcut AD model decays with increasing pore 
@@
 %  realizations in order to generate each point in Figure~\ref{fig:flux_curves_ad}, 
-%  however, in Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting information,
+%  however, in Figure~\ref{S-fig:flux_curve_sensitivity} of the Supplemental Material,
 %  we show that one can still show statistically significant differences in solute 
@@
 
-  %BJC6: TODO: add (a), (b), (c) labels
-  %BJC7: TODO: optimize figure dimensions
   \begin{figure}
   \centering
-  \begin{subfigure}{\textwidth}
-  \includegraphics[width=\textwidth]{hurst_beta_variations.pdf}
-  \caption*{}\label{fig:beta_hurst}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{beta_hurst_scatter.pdf}
+  \caption{}\label{fig:beta_hurst}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{beta_variations.pdf}
+  \caption{}\label{fig:beta_hurst}
   \end{subfigure}
@@
   %BJC7: I could plot bars with the MSD of each solute to show that trend is same.
+  \vspace{-0.25cm}
   \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
-  \caption*{}\label{fig:c_parameters}
+  \caption{}\label{fig:c_parameters}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{c_influence.pdf}
-  \caption*{}\label{fig:c_influence}
-  \end{subfigure}
-  \vspace{-1.5cm}
+  \caption{}\label{fig:c_influence}
+  \end{subfigure}
+  \vspace{-.5cm}
   %MRS8: top figure is very confusing (also, I see a check in the urea green bar?) 
-  \caption{(top) Increased anti-correlation between hops (decreased $H$) appears to 
+  \caption{(a) Increased anti-correlation between hops (decreased $H$) appears to 
   increase the length-dependence of solute flux (higher $\beta$) for the sFBMcut model.
-  If we remove anti-correlation, by setting $H$=0.5, the length dependence parameter
+  (b) If we remove anti-correlation, by setting $H$=0.5, the length dependence parameter
   drops to a value near 2. When we remove hop anti-correlation and dwell times between
@@
   This suggests that $\beta$ does not depend on dwell times (parameterized by $\alpha$
-  and $\lambda$). (bottom left) As solute flux increases, the scaling of the flux 
+  and $\lambda$). (c) As solute flux increases, the scaling of the flux 
   curves, $A$, increases (compare ranking with Figure~\ref{fig:flux_curves_ad}).
-  (bottom right) Physical processes which increase the rate of solute displacement 
+  (d) Physical processes which increase the rate of solute displacement 
   result in larger values of $A$. To test the dependence of $A$ on $\alpha$, $\sigma$, 
@@
 
-  \caption{The selectivity 
-    %MRS8:
-    %of 2 species 
-    between pairs of species
-    changes monotonically with pore length. The
-  strength of dependence on pore length depends on the difference between $\beta$ values.
-  The selectivities predicted by the sFBMcut AD model (a) are much larger in magnitude than
-  %MRS8: you removed MSDDM from figure.
-  those predicted by the MSDDM (b) because predictions of the AD model result in a much
-  larger variation in flux (compare Figures~\ref{fig:flux_curves_ad}).}
+  \caption{The selectivity between pairs of species changes monotonically with pore length. 
+  The strength of dependence on pore length depends on the difference between $\beta$ values.
+  Largest differences in solute flux result in high selectivites at any pore length.
+  This membrane may be a good candidate for the separation of ethylene glycol from acetic
+  acid. Ethylene glycol has the lowest $\beta$ value while acetic acid has the second highest, 
+  leading to strong length dependence. Ethylene glycol also has the highest flux and acetic acid
+  has the lowest resulting in relatively high selectivities independent of pore length.}
   \label{fig:selectivity}
@@
   behavior (lower $\beta$). The selectivity towards solutes with less length dependent flux
-  increases with membrane thickness. In most cases, the length dependence of selectivity 
-  plateaus quickly which implies that a coating of LLC membrane with a thickness on the 
-  order of those already made experimentally should be sufficiently 
-  %MRS8: optimal isn't really defined here.
-  optimal.
+  increases with membrane thickness. 
+  %BJC8: modified
+  In most cases, the length dependence of selectivity plateaus near or within the range of 
+  experimentally-accessible membrane thicknesses. Therefore, from a practical standpoint, 
+  one should not expect significant changes in selectivity by varying LLC membrane thickness.
+
+%  before  which implies that a coating of LLC membrane with a thickness on the 
+%  order of those already made experimentally should be sufficiently 
+%  optimal.
 
@@
   %MRS8: separations. Even if the models aren't quite right, they show how such selectivtiy CAN arise.
-  %BJC7: I don't know why there is a big space before this paragraph when compiled
+  %BJC8: added a new paragraph after this one.
+
   Of the solutes studied, the data suggests that this particular LLC membrane 
@@
   dependence of selectivity.
+
+  The insights into flux and selectivity provided by our time series modeling approach
+  could not be drawn easily by simply observing solute motion, the structure of the 
+  membrane nanopores, or even the solute trajectories extracted from the MD
+  simulations. Differences in solute MSDs alone do not fully explain the trends and 
+  magnitudes of the selectivities shown in Figure~\ref{fig:selectivity}.
+  Complex interplay between membrane constituents and solutes with varying
+  chemical functionality lead to diverse solute behavior. Even if our model is 
+  not perfect, it provides clear logic behind the mechanisms leading to selective
+  behavior which is very important for design. We hope this type of analysis can
+  be leveraged to explore new, interesting and complex separations problems.
+
   %In both case, selectivity is enhanced as the pore 
@@
   distributions for each type of transition, but this would require orders of magnitude
-  more data. 
-  %MRS8: (could add something lie below) 
-  %MRS8: or more prior assumptions about the distributions.
+  more data or more prior assumptions about the distributions.
   This approach is further complicated by the need to make correlated draws
@@
   %MRS8: ``the AD model'' vs approach, since it's multiple models.
-  Although the AD model generates qualitatively accurate trajectories and 
+  Although the AD approach generates qualitatively accurate trajectories and 
   predicts MSDs near or within the 1$\sigma$ confidence interval of our
-  MD simulations, the curvature of the predicted MSDs 
-  %MRS8: maybe ``does not appear to be consistent''?
-  may not be consistent
+  MD simulations, the curvature of the predicted MSDs does not appear to be consistent
   with the MD simulations. The MSD curves calculated from MD simulations 
-  appear to straighten out on long timescales while those predicted by the
-  AD model continuously curve. This is because pure fractional Brownian motion
+  appear to straighten out on long timescales while those predicted
+  AD models continuously curve. This is because pure fractional Brownian motion
   features hop correlation that persists indefinitely. We may be able to address
   this by truncating the positional autocorrelation function, allowing 
-  correlation to diminish on the 100 ns timescale. 
-  %MRS8: maybe add something like ``as suggested by the physical trajectories and the structural model''?
+  correlation to diminish on the 100 ns timescale as suggested by the physical 
+  trajectories.
 
@@
   of ethylene glycol from acetic acid or methanol.
-
-%  This length dependence may dissipate once we gain a more 
-%  complete understanding of the hop correlation structure. 
-%  If the length dependence of a properly correlated model always converges to 
-%  $\beta$=2, it will greatly influence the prediction of selectivity on 
-%  macroscopic length scales.
-%  However, this length dependence mostly plateaus at length scales that can be
-%  synthesized experimentally. The data suggests that this particular membrane 
-%  may be useful for separating ethylene glycol and acetic acid.
 
@@
   to design LLC monomers for solute-specific separations by forcing us to think
-  in terms of controlling solute transport. The anomalous diffusion model is 
+  in terms of controlling solute transport. The anomalous diffusion modeling approach is 
   quite flexible because it does not require knowledge of specific trapping 
@@
   %MRS8: I wonder if the 2 mode model can be considered a intermediate - a bit of structural information is involved.
-  model can help uncover trapping mechanisms by forcing the scientist to 
+  approach can help uncover trapping mechanisms by forcing the scientist to 
   identify features common to solutes with long or short hop lengths and dwell
@@
 
-  \section*{Supporting Information}
+  \section*{Supplemental Material}
 
   Detailed explanations and expansions upon the results and procedures mentioned in
-  the main text are described in the Supporting Information. This information is
+  the main text are described in the Supplemental Material. This information is
   available free of charge via the Internet at http://pubs.acs.org.
@@
 
-  %MRS6: look over and make bibliography consistent (i.e. no months, consistent journal abbreviations)
-  \bibliographystyle{apsrev4-2}
+  %\bibliographystyle{apsrev4-2}
   \bibliography{stochastic_transport}
@@
 
-  %BJC5: still a work in progress
-  %MRS6: seems pretty reasonable as a concept.
-If you can make the three figure labels the same color (doesn't have to be black or white) and same font, might be nice.
-Maybe make arrows more like circle arcs, and change the color from black so it stands out more?
-The time series model figure is a bit busy.
-Can it be reduced from 4 subfigures?
-May not be necessary, but one thing to think about.
   \begin{figure}[!htb]

### 2020-01-23 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Incorporated MRS comments

@@
   \texttt{/analysis/ Markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
-  \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD or MSDDM model. \\\hline
-%MRS8: see main text discussion about ``the XXXX model''  
+  \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD approach. \\\hline 
   \end{tabular}
@@
   \end{subfigure}  
-  %MRS8: make clear in (b) the lines all lay on top so people don't miss it.  
   \caption{(a) The analytical autocorrelation function of FBM decays to zero faster
@@
   FLM process does not change with increasing sequence length (N). It shares the same
-  autocorrelation function as fractional Brownian motion (FBM). All 
-  %sequenced
-  sequences 
-  used to
-  make this plot were generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
+  autocorrelation function as fractional Brownian motion (FBM). Note that all lines
+  plotted lie on top of each other. All sequences used to make this plot were generated
+  using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
   \end{figure}
@@
 
+  We validated both the 1 and 2 mode AD models with urea and acetic acid, since their
+  trajectories appear stationary. The MSDs resulting from 1000 realizations of the AD
+  model are shown in Figure~\ref{fig:train_test}. We consider the model's prediction 
+  to match well if the MSD lies within the 1$\sigma$ confidence intervals of the MD MSDs.
+  We also look for qualitative agreement in the shape of the curves.
+
+  The models are capable of reasonably predicting the MD MSD values of the second
+  half of the solute trajectories based on parameters generated from the first half
+  when the dwell time distributions are parameterized by a power law with an 
+  exponential cut-off. At long timescales, the MSD of urea is under-predicted 
+  for both the 1 and 2 mode models with the same true of acetic acid on short 
+  timescales. Without truncation of the power law distribution, the MD 
+  MSDs are underestimated in all cases because dwell times on the order of the
+  MD simulation length are sampled and incorporated into the simulated anomalous
+  diffusion trajectories.
+
   \begin{figure}[h]
@@
 
-  We validated both the 1 and 2 mode AD models with urea and acetic acid, since their
-  trajectories appear stationary. The MSDs resulting from 1000 realizations of the AD
-  model are shown in Figure~\ref{fig:train_test}. We consider the model's prediction 
-  to match well if the MSD lies within the 1$\sigma$ confidence intervals of the MD MSDs.
-  We also look for qualitative agreement in the shape of the curves.
+  \newpage
 
@@
   \end{subfigure} 
-  %MRS6: I'm not sure I see red in urea.  Is the uncertainty that low?
-  %BJC6: I think red and orange are directly on top of each other with same error bars
-  %MRS8: point out that the _cut data is the same as the data in the main tex. 
   \caption{In most cases, when using power laws with exponential cut-offs 
@@
   under-predicted at long timescales and those of acetic acid to be under-predicted
-  at short timescales.}\label{fig:train_test}
-  \end{figure}
-
-  The models are capable of reasonably predicting the MD MSD values of the second
-  half of the solute trajectories based on parameters generated from the first half
-  when the dwell time distributions are parameterized by a power law with an 
-  exponential cut-off. At long timescales, the MSD of urea is under-predicted 
-  for both the 1 and 2 mode models with the same true of acetic acid on short 
-  timescales. Without truncation of the power law distribution, the MD 
-  MSDs are underestimated in all cases because dwell times on the order of the
-  MD simulation length are sampled and incorporated into the simulated anomalous
-  diffusion trajectories. Considering the longest observed dwell time among all
-  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
+  at short timescales. Note that the sFBMcut and sFLMcut models are the same as 
+  those in the main text.}\label{fig:train_test}
+  \end{figure}
+
+  %Considering the longest observed dwell time among all
+  %solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
   %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
@@
 
-  From a qualitative perspective, the models only have moderate success at predicting
-  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
-  the error in the predicted MSD magnitudes. The curves predicted for urea with both 1 
-  and 2 modes appear to have too much curvature, which causes it to under-predict the 
-  MSD at long timescales, while those of acetic acid lack curvature, leading the
-  AD model to under-predict the MSD at short timescales.
+%  From a qualitative perspective, the models only have moderate success at predicting
+%  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
+%  the error in the predicted MSD magnitudes. The curves predicted for urea with both 1 
+%  and 2 modes appear to have too much curvature, which causes it to under-predict the 
+%  MSD at long timescales, while those of acetic acid lack curvature, leading the
+%  AD model to under-predict the MSD at short timescales.
 
   %MRS8: how much of this is already in the main text?  Try to limit analysis that appears in the main text.
-  The under-estimate of urea's MSD at long timescales is due to long timescale
-  positional anti-correlation which may not be present in the molecularly 
-  detailed simulations of the system. The 
-  %MRS6: I'm not following whether or not there should be positional anti-correlation.  I was thinking there should be,
-  %but perhaps I'm misunderstanding something here? 
-  persistent curvature of the predicted MSD curves is a direct consequence of 
-  the Hurst parameter. Without anti-correlation, the process would be 
-  a pure CTRW for which one would expect the time averaged MSD curves to become 
-  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
-  positional correlation is lost which would manifest as a transition from a sub-linear
-  to linear MSD curve. A solution for more accurately modeling this behavior in  
-  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}
-
-  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
-  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
-  because the Hurst parameter is challenging to quantify, especially with a relatively 
-  small amount of data (see Section~\ref{M-method:sfbm} of the main text for further discussion of this 
-  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
-  but also lower the predicted MSD meaning we are either underestimating the width of
-  the hop length distribution, favoring longer dwell times, or both.
-
-  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
-  a real system, positional anti-correlation may dissipate after a sufficiently long 
-  time lag, dependent on the solute being studied. Second, it is difficult to reliably
-  parameterize the Hurst parameter which is important for accurately describing the 
-  curvature of the solute MSDs.
-
-  This analysis also suggests that working with only half of the data we collected
-  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
-  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
-  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
-  sFLMcut), but still appear to systematically under-predict the mean. We may be
-  operating on the border of the minimum amount of data required to accurately 
-  parameterize the AD model. Longer simulations and more independent trajectories may
-  be necessary. Therefore, in the next section we will work with parameters fit to the
-  full equilibrated portion of the solute trajectories, doubling the data.
+%  The under-estimate of urea's MSD at long timescales is due to long timescale
+%  positional anti-correlation which may not be present in the molecularly 
+%  detailed simulations of the system. The 
+%  persistent curvature of the predicted MSD curves is a direct consequence of 
+%  the Hurst parameter. Without anti-correlation, the process would be 
+%  a pure CTRW for which one would expect the time averaged MSD curves to become 
+%  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
+%  positional correlation is lost which would manifest as a transition from a sub-linear
+%  to linear MSD curve. A solution for more accurately modeling this behavior in  
+%  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}
+%  
+%  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
+%  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
+%  because the Hurst parameter is challenging to quantify, especially with a relatively 
+%  small amount of data (see Section~\ref{M-method:sfbm} of the main text for further discussion of this 
+%  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
+%  but also lower the predicted MSD meaning we are either underestimating the width of
+%  the hop length distribution, favoring longer dwell times, or both.
+%  
+%  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
+%  a real system, positional anti-correlation may dissipate after a sufficiently long 
+%  time lag, dependent on the solute being studied. Second, it is difficult to reliably
+%  parameterize the Hurst parameter which is important for accurately describing the 
+%  curvature of the solute MSDs.
+%  
+%  This analysis also suggests that working with only half of the data we collected
+%  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
+%  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
+%  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
+%  sFLMcut), but still appear to systematically under-predict the mean. We may be
+%  operating on the border of the minimum amount of data required to accurately 
+%  parameterize the AD model. Longer simulations and more independent trajectories may
+%  be necessary. Therefore, in the next section we will work with parameters fit to the
+%  full equilibrated portion of the solute trajectories, doubling the data.
 
@@
 
-  \newpage
-
-  %MRS8: I think just ``Tables of Anomalous''.  Tabular sounds like it's a kind of anomalous diffusion.
-  \section{Tabular Anomalous Diffusion Parameters}\label{section:tabular_AD_params}
+  \clearpage
+
+  \section{Tables of Anomalous Diffusion Parameters}\label{section:tabular_AD_params}
 
   %MRS8: representations of the parameters, or representations of the graphs?  Or just tabulations of the data found in the graph.
-  The tables in the section are tabular representations of the parameters depicted
-  in Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the 
-  main text.
+  The tables in this section are tabular representations of the parameters depicted in
+  Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the main text
+  and used to generate AD approach realizations whose MSDs are shown in Figure~\ref{M-fig:anomalous_msds}
+  of the main text.
 
@@
   \end{tabular}
-  %MRS: to what extent are these captions the same as the captions to equivalent graphs main text?
-If it's the same, you probably should say so; if different, there should be some justification for the differences, and should be mentioned in the main text that more information is here.
-  \caption{To create a 1 mode model for each solute, we parameterized a pure power
-  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
-  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
-  law tails and higher values of $\lambda$ truncate the distribution at lower
-  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
-  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
-  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
-  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
-  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
-  function ($\gamma(H)$) to describe the degree of correlation between hops. 
-  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
+  \caption{Parameters of the one mode AD approach models. See the main
+  text for further details.}\label{table:sfbm_params}
   \end{table}
@@
   \end{tabular}
-  \caption{The two model parameterizes solute behavior in the pores and tails separately. 
-  Generally, movement is much more restricted in the tail region. To create a 2 mode model,
-  we generated a set of parameters based on solute behavior as function of distance from
-  the pore center. Mode 1 corresponds to solute behavior within 0.75 nm of the pore center
-  and mode 2 corresponds to behavior greater than or equal to 0.75 nm from the pore center.
-  Note that we used the same Hurst parameter for both modes due to a low number of 
-  sufficiently long sequences of hops in each mode. See Table~\ref{table:sfbm_params} for
-  descriptions of the parameters.}\label{table:sfbm_params_2mode}
+  \caption{Parameters of the 2 mode AD approach models. See the main text for further
+  details.}\label{table:sfbm_params_2mode}
   \end{table}
@@
   \newpage
-  %MRS8: ``Table of''. Same comments about captions being the same or different, since the data should be the same.
-  \section{Tabular MSDDM parameters}\label{section:msddm_params}
+  \section{Table of MSDDM parameters}\label{section:msddm_params}
 
@@
   trajectories and used them to generate realizations of our MSDDM model. The states
-  are defined in Table~\ref{M-table:states} of the main text except state T which describes the transition
-  emissions.}\label{table:msddm_params}
+  are defined in Table~\ref{M-table:states} of the main text except state T which 
+  describes the transition emissions.}\label{table:msddm_params}
   \end{table}
@@
   %MRS8: fig:msddm_fpt_fits is commented out?  Or xr not working should this be main text?
-  In Figures~\ref{fig:ad_fpt_fits} and~\ref{fig:msddm_fpt_fits}, we demonstrate
+  %BJC8: yeah because 
+  In Figure~\ref{fig:ad_fpt_fits} 
+  %and~\ref{fig:msddm_fpt_fits},  % BJC8: didn't do solute flux with MSDDM so why mention
+  we demonstrate
   the high quality of our analytical fits of Equation~\ref{eqn:passage_times} to 
   the distribution of solute first passage times derived from both the AD
-  and MSDDM models. The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
-  relatively noisy because we only generated 1000 realizations of the MSDDM 
-  versus 10000 of the AD model. In Figure~\ref{fig:flux_curve_sensitivity}, we
-  justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
-  model realizations to show that one needs as few as 100 independent trajectory
+  and MSDDM models. 
+  %The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
+  %relatively noisy because we only generated 1000 realizations of the MSDDM 
+  %versus 10000 of the AD model. 
+  In Figure~\ref{fig:flux_curve_sensitivity}, we
+  %justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
+%  model realizations to 
+  show that one only needs as few as 100 independent trajectory
   realizations at each pore length in order to reliably fit Equation~\ref{eqn:passage_times}

### 2020-01-24 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Responded to comments.

@@
 Use lower-case roman letters for footnotes placed at the bottom of a table.
-
+%MRS9: I'd go with what they said.  Looking at PRE, it looks like you can put double lines above and below the table, though - I added them 
   \begin{table}[!htb]
@@
 	  \begin{tabular}{ccc}
-	  %\hline
+            \hline
+	  \hline
 	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
@@
       Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
-	  %\hline
+	  \hline
+          \hline
 	  \end{tabular}
@@
 	  into all models.}\label{table:anomalous_models}
+
  \end{table}
@@
   %BJC3: not sure how to cite fbm
+  %MRS9: cite github page?
   We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
@@
   %BJC8: reformatted. I think this is what they want in terms of format
+  %MRS9: tweaked 
   \begin{table}[!htb]
@@
 	  \begin{tabular}{ll}
+            \hline
+            \hline
 	  \multicolumn{2}{c}{Markov State-Dependent Dynamical Model State Definitions} \\
@@
 	  4. In tails, hydrogen bonding and associated  ~~~~& 8. In pores, hydrogen bonding and associated \\
-	  %\hline
+	  \hline
+          \hline
 	  \end{tabular}
@@
   %BJC8: I thought that sFBMcut and sFLMcut implied which distributions I used. It's in Table I
+  %MRS9: Maybe say ``both the Brownian (sFBMcut) and Levy (sFBMcut) version of both the one and two AD models''.
+I think with the number of models floating around, it helps to be super explicit about what is being considered at any point.
   In most cases, the sFBMcut and sFLMcut models give very similar results, most 
@@
   %BJC8: I'm interpreting this as, "how does this information relate to design" 
+  %MRS9: yes.
   Urea spends the largest fraction of its time trapped via association with sodium ions.
@@
   %BJC8: something like this I think.   
-  Therefore the transport rate of urea may be enhanced the most by removing or changing 
+  Therefore the transport rate of urea 
+  %MRS9 tweak.
+  %may be enhanced the most
+  is likely to be most significantly modified
+  by removing or changing 
   the counter-ion identity.
-  %MRS8: above seems incomplete - are weak h-bond donors so what?
 
@@
   %BJC8: added following sentence
+  %MRS9: as above, maybe ``modified'' is the best rather than enhanced?  Maybe we want to slow it down as well. 
   The transport rate of ethylene glycol might be increased by removing hydrogen 
@@
   %BJC8: added  
+  %MRS9: see above.
   If one desires an increased methanol transport 
@@
   %BJC8:added  
+  %MRS9: see above.
   As with ethylene glycol, one might increase
   the transport rate of acetic acid by removing hydrogen bond accepting constituents
-  of the LLC monomer. With this modification, we hypothesize that acetic acid would 
+  of the LLC monomer. With this modification, we hypothesize that acetic acid 
+  %MRS9: 
+  %would 
+  might 
   show similar transport rates to urea given their structural similarity.
@@
   %BJC8: added a new paragraph after this one.
+  %MRS9: looks good.
 

### 2020-01-24 Ben_Manuscripts/stochastic_transport/cover_letter.tex
some tweaks to cover letter.
Cover letter updates with referees

@@
 
-	%\noindent May 3\textsuperscript{rd}, 2019\\
-	\noindent \date
+	\noindent January 27\textsuperscript{th}, 2020\\
+	%\noindent \date
 
-	\noindent Dear Editors,\\
+	\noindent Dear Editors, \\
 
@@
 
-	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael R.
-	Shirts, for	consideration for publication as a Research Article in Physical 
-	Review E. We expect this work to be of significant interest to researchers 
-	who study complex dynamics in both structured and amorphous soft materials.
+	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and
+	Michael R.  Shirts, for consideration for publication as a Research
+	Article in Physical Review E. We expect this work to be of significant
+	interest to researchers who study complex dynamics in both structured
+	and amorphous soft materials. \\
 
-	In this article, we use solute trajectories generated from 5$\mu$s molecular
-	dynamics (MD) simulations of an inverted hexagonal (H\textsubsript{II}) phase
-	self-assembled lyotropic liquid crystal (LLC) polymer membrane in order to 
-	parameterize two different stochastic time series models capable of predicting
-	solute flux and selectivity on a macroscopic scale. Realizations of both models
-	quantitatively reproduce the mean squared displacements (MSDs) exhibited by 
-	solutes in MD simulations. This is among the first studies to apply time 
-	series modeling approaches in order to predict bulk materials properties.
+	In this article, we use 5$\mu$s molecular dynamics (MD) simulations of
+	solutes moving through the pores of an inverted hexagonal phase
+	lyotropic liquid crystal (LLC) polymer membrane in order to
+	parameterize two different stochastic time series models capable of
+	predicting solute flux and selectivity on a macroscopic scale.
+	Realizations of both models quantitatively reproduce the mean squared
+	displacements (MSDs) exhibited by the solutes in our MD simulations. We then
+	demonstrate how we can use realizations orders of magnitude longer than
+	our MD simulations in order to predict solute flux and selectivity.
+	This is among the first studies to apply time series modeling
+	approaches in order to predict bulk materials properties. \\
 
-	Recently, we characterized transport mechanisms exhibited by a series of 
-	small polar solutes in an LLC Membrane (Coscia and Shirts \textit{J. Phys.
-	Chem. B}, 123, 6314--6330 (2019)). We observed subdiffusive solute transport
-	characterized by intermittent hops separated by periods of entrapment. In
-	this work, we build on the chemical intuition gained from our previous study
-	in order to formulate stochastic models which produce trajectory realizations
-	that share the same dynamical properties as those exhibited by solutes in 
-	our MD simulations. We explore two modeling approaches. First, based on the
-	anomalous diffusion literature, we hypothesize that solutes are subject 
-	to subordinated fractional Brownian or L\'evy motion. This implies that 
-	solutes experience a series of dwell times separated by anti-correlated hop
-	lengths. Our second approach adds state-dependent dynamics to standard Markov
-	state modeling approaches. We model solute motion as a series of transitions
-	between various trapped states, each with different dynamical properties.
-
-%        Recently, we characterized an atomistic molecular model of an
-%        LLC membrane that is maximally consistent with experimental
-%        observations (Coscia et al. \textit{J. Phys. Chem. B}, 123,
-%        289--309 (2019)). In this work, we observe and quantify
-%        transport of water, sodium and 20 small polar solutes within
-%        the pores of our atomistic H\textsubscript{II} phase LLC
-%        membrane model. In general, all solutes exhibit subdiffusive
-%        transport behavior characterized by intermittent hops between
-%        long periods of entrapment. However, due the pores'
-%        inhomogeneous architecture, we observed 3 different mechanisms
-%        of entrapment. First, solutes can diffuse out of the pores and
-%        become entangled between tails. Second, many of the solutes
-%        are capable of donating hydrogen bonds to monomer head groups
-%        for extended periods of time. Finally, solutes can associate
-%        with monomer head group counter-ions within nanopores. Each
-%        solute is influenced by each mechanism to varying degrees
-%        dependent on its size and chemical functionality. We begin our
-%        discussion with a broad description of these mechanisms in the
-%        context of all solutes before restricting the discussion to
-%        more detailed analyses of subsets of chemically-similar
-%        solutes.
+	Based the chemical intuition gained from our previous studies, we
+	formulate the stochastic models so that they share the same dynamical
+	properties as those exhibited by solutes in our MD simulations. 
+	Recently, we characterized transport mechanisms exhibited by a series
+	of small polar solutes in an LLC Membrane (Coscia and Shirts \textit{J.
+	Phys. Chem. B}, 123, 6314--6330 (2019)). We observed subdiffusive
+	solute transport characterized by intermittent hops separated by
+	periods of entrapment. 
+	%In this work, we build on the chemical intuition
+	%gained from our previous study in order to formulate stochastic models
+	%which produce trajectory realizations that share the same dynamical
+	%properties as those exhibited by solutes in our MD simulations. 
+	In this work, we explore two approaches for modeling this behavior.
+	First, based on the anomalous diffusion literature, we hypothesize that
+	solutes are subject to either subordinated fractional Brownian or
+	L\'evy motion. This implies that solutes experience a series of dwell
+	times separated by anti-correlated hop lengths. Our second approach
+	adds state-dependent dynamics to standard Markov state modeling
+	approaches. We model solute motion as a series of transitions between
+	various trapped states, each with different dynamical properties. \\
 
@@
 
-		\item Menachem Elimelech is a leader in the development of membrane technologies
-		for	water desalination and water reuse (Yale University, 203-432-2789,
-		\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).
+		\item Ralf Metzler is an expert in anomalous diffusion theory
+			with applications to soft materials. (University of
+			Potsdam, \href{mailto:kakania@uni-potsdam.de}{kakania @
+			uni-potsdam.de})
 
-		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
-		and various	nanostructured materials (Northeastern University, 617-373-8619 	
-		\href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})
+		\item Aziz Ghoufi has studied molecular mechanisms of
+			subdiffusive solute transport in nanostructured
+			materials. (Institut de Physique de Rennes,
+			\href:{mailto:aziz.ghoufi@univ-rennes1.fr}{aziz.ghoufi@univ-rennes1.fr})
 
-		\item Mahesh Mahanthappa has experience modeling soft materials using molecular dynamics
-		including work on ion transport in various ordered liquid crystalline phases. 
-		(University of Minnesota, 612-625-4599,\href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})
+		%BJC: elimelech is more experiment-focused
+		%\item Menachem Elimelech is a leader in the development of
+		%	membrane technologies for water desalination and water
+		%	reuse (Yale University, 203-432-2789,
+		%	\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).
+
+		\item Richard Lueptow uses molecular simulations to understand
+			transport processes in polymeric nanofiltration and
+			reverse osmosis membranes. (Northwestern University
+			\href{mailto:r-lueptow@northwestern.edu}{r-lueptow@northwestern.edu})
+
+		%BJC: I don't think Paddison is as strong as the others
 

### 2020-01-26 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Final readthrough completed

--- 2020-01-23 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
@@
   dwell times, hop lengths between dwells and correlation between hops. We 
-  explore two variations of the anomalous diffusion model. The first variation
+  explore two variations of the anomalous diffusion modelling approach. The first variation
   applies a single set of parameters to the solute displacements and the second
@@
   configurational state of the system as a Markov process, each
-  of which has separate transport properties. For each state and transition
+  of which having separate transport properties. For each state and transition
   between states, we parameterize the distribution and temporal correlation 
@@
 
-  Highly selective separations membranes are desirable in numerous applications. 
-  The ability to efficiently separate ions from saline water sources using membranes 
-  has been actively pursued for years in an effort to create potable water for people 
-  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
-  municipal water supplies, there is a need for membranes that can specifically separate
-  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
-  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
-  there is a strong interest in creating breathable fabrics which selectively allow 
-  passage of water vapor.~\cite{mondloch_destruction_2015}
-
-  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
-  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
-  They may provide a promising alternative to conventional membrane separation techniques
-  by being selective based not only on solute size and charge, but on solute chemical 
-  functionality as well.~\cite{dischinger_application_2017} One can tune the functionality
-  of LLC monomers in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
-  Two general morphologies of LLC membranes are being actively developed. The inverted hexagonal, 
-  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
-  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
-  throughput separations. Unfortunately, aligning the microscopic hexagonal mesophases on 
-  a large scale as required for high permeability has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
-  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
-  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
-  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
-  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
-  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.~\cite{hatakeyama_nanoporous_2010}
-
-  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
-  membranes using the available chemical space of LLC monomers. To date, only a limited 
-  subset of LLC monomers have been studied experimentally in membrane applications.
+  Highly selective separations membranes are desirable in numerous
+  applications. The ability to efficiently separate ions from saline water
+  sources using membranes has been actively pursued for years in an effort to
+  create potable water for people in water-scarce
+  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
+  supplies, there is a need for membranes that can specifically separate
+  potentially harmful organic micropollutants such as fertilizers, pesticides,
+  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} In
+  the materials industry, there is a strong interest in creating breathable
+  fabrics which selectively allow passage of water
+  vapor.~\cite{mondloch_destruction_2015}
+
+  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
+  can be cross-linked into mechanically strong and highly selective nanoporous
+  membranes.~\cite{gin_polymerized_2008} They may provide a promising
+  alternative to conventional membrane separation techniques by being selective
+  based not only on solute size and charge, but on solute chemical
+  functionality as well.~\cite{dischinger_application_2017} One can tune the
+  functionality of LLC monomers in order to enhance or weaken specific
+  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
+  morphologies of LLC membranes are being actively developed. The inverted
+  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
+  pores on the order of 1 nm in size. A perfectly synthesized
+  H\textsubscript{II} phase has an ideal geometry for high throughput
+  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
+  a large scale as required for high permeability has shown limited
+  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
+  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
+  complex pores of the H\textsubscript{II} phase but its geometry consists of a
+  tortuous network of 3D interconnected pores which do not require
+  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
+  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
+  H\textsubscript{II} phase, it is considerably easier to synthesize at
+  scale.~\cite{hatakeyama_nanoporous_2010}
+
+  Molecular modeling may make it possible to efficiently evaluate
+  solute-specific separation membranes using the available chemical space of
+  LLC monomers. To date, only a limited subset of LLC monomers have been
+  studied experimentally in membrane applications.
   \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
-  Even within this small subset, they have demonstrated selectivities that could not be
-  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
-  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
-  interactions that are key to separation mechanisms, allowing us to move beyond 
-  Edisonian design approaches.
-
-  In our previous work,~\cite{coscia_chemically_2019} we used molecular dynamics (MD) 
-  simulations to study the transport of 20 small polar molecules in an H\textsubscript{II}
-  phase LLC membrane. We chose to study the H\textsubscript{II} phase because it is
-  a simpler geometry to model than the Q\textsubscript{I} phase and significantly more
-  structural data is available to help ensure molecular models are consistent with experiment.
-  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
-  separated by periods of entrapment. We identified three mechanisms responsible for the 
-  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
-  head groups, and association with the monomer's sodium counter ions.
+  Even within this small subset, they have demonstrated selectivities that
+  could not be explained beyond speculation and vague empirical
+  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
+  can provide the resolution necessary to identify molecular interactions that
+  are key to separation mechanisms, allowing us to move beyond Edisonian design
+  approaches.
+
+  In our previous work,~\cite{coscia_chemically_2019} we used molecular
+  dynamics (MD) simulations to study the transport of 20 small polar molecules
+  in an H\textsubscript{II} phase LLC membrane. We chose to study the
+  H\textsubscript{II} phase because it is a simpler geometry to model than the
+  Q\textsubscript{I} phase and significantly more structural data is available
+  to help ensure molecular models are consistent with experiment. In general,
+  we observed subdiffusive transport behavior characterized by intermittent
+  hops separated by periods of entrapment. We identified three mechanisms
+  responsible for the solute trapping behavior: entanglement among monomer
+  tails, hydrogen bonding with monomer head groups, and association with the
+  monomer's sodium counter ions.
 
@@
   quantitative predictions of macroscopic observables such as solute flux and
-  selectivity. Due to the size of the types of systems we are studying (at least
-  (62,000 atoms) it is prohibitively expensive and time-consuming to
-  run simulations longer than those performed for this work ($\sim$5 $\mu$s). 
-  Even with the relatively large size of our system, we only simulate 24 solute trajectories per unit cell in order
-  to minimize solute-solute interactions. This results in relatively high uncertainties
-  in observables such as mean squared displacement (MSD), preventing reliable long
-  timescale predictions. We are in need of a way of studying the collective motion
-  of a much larger set of solutes over much longer timescales.
-
-  Mathematical descriptions of transport in complex separations membranes are 
-  a powerful way to understand mechanisms and formulate design principles. 
+  selectivity. Due to the size of the types of systems we are studying (at
+  least (62,000 atoms) it is prohibitively expensive and time-consuming to run
+  simulations longer than those performed for this work ($\sim$5 $\mu$s).  Even
+  with the relatively large size of our system, we only simulate 24 solute
+  trajectories per unit cell in order to minimize solute-solute interactions.
+  This results in relatively high uncertainties in observables such as mean
+  squared displacement (MSD), preventing reliable long timescale predictions.
+  We are in need of a way of studying the collective motion of a much larger
+  set of solutes over much longer timescales.
+
+  Mathematical descriptions of transport in complex separations membranes are a
+  powerful way to understand mechanisms and formulate design principles.
   \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
-  The complexity of a well-fit model generally parallels the complexity of the transport 
-  mechanism being studied, as well as the transport information the model conveys.
-  In dense homogeneous membranes, the solution-diffusion model can extract 
-  diffusion and partition coefficients and has successfully predicted solute 
-  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
-  models yield predictions of diffusion coefficients and solute transport rates 
-  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
-  tracking approaches have taken researchers beyond continuum modeling allowing them to 
-  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
-  level, one can use molecular dynamics (MD) simulations to study both single 
-  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
-  All of these approaches facilitate generation of hypotheses about the
-  molecular origins of separations by attempting to give a more intuitive 
-  understanding of how solutes move as a function of their environment, in turn
-  suggesting experiments that could be performed.
-
-  Using a bottom-up modeling approach, we can parameterize single particle behavior
-  by extracting their trajectories from MD simulations and studying the properties that
-  have the greatest influence on solute dynamics. With this information, we can learn
-  how to construct an ensemble of characteristic single solute trajectories with these
-  properties which would be useful for making long timescale predictions with computational
-  ease and lower uncertainties. Fortunately, there is an abundance of information encoded
-  in the complex solute trajectories. We can incorporate fluctuations and time-dependent 
-  correlations in solute position as well as the length of time solutes are trapped into a
-  model. We can add further detail by integrating our time series analysis with our 
-  knowledge of the primary trapping mechanisms as well as the solute's changing chemical
-  environment within the heterogeneous membrane.
-
-  %MRS8: really nice flow in the introduction up through here.
-%  By reducing our MD simulations to observations of several key properties that 
-%  have the greatest influence on solute dynamics, we can construct many realizations
-%  of single solute trajectories useful for making long timescale predictions with 
-%  computational ease and lower uncertainties. Fortunately, there is an abundance of 
-%  information encoded in the complex solute trajectories. Into a model, we can 
-%  incorporate fluctuations and time-dependent correlations in solute position as well
-%  as the length of time solutes are trapped. We can add further detail by integrating
-%  our time series analysis with our knowledge of the primary trapping mechanisms as
-%  well as the solute's changing chemical environment within the heterogeneous membrane.
-
-  In this work, we use the output of our MD simulations to construct two classes of 
-  mathematical models which aim to predict membrane performance while providing quantitative 
-  mechanistic insights. The functional form of these models is driven by mechanistic 
-  observations from our previous work and their inputs are parameterized using a 
-  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations.
-
-  We constructed our first model by applying the rigorous theoretical foundation 
-  already developed to describe the motion of particles exhibiting non-Brownian, or
-  anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990}
-  The tools introduced by fractional calculus are instrumental to this theory.~\cite{gorenflo_fractional_1997}
-  They allow us to generalize the normally linear diffusion equation to fractional
-  derivative orders, providing descriptions of a much more diverse set of behavior,
-  including subdiffusion, a type of anomalous diffusion exhibited by solutes in 
-  this study.~\cite{klages_anomalous_2008}
+  The complexity of a well-fit model generally parallels the complexity of the
+  transport mechanism being studied, as well as the transport information the
+  model conveys. In dense homogeneous membranes, the solution-diffusion model
+  can extract diffusion and partition coefficients and has successfully
+  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
+  Analogously, pore-flow models yield predictions of diffusion coefficients and
+  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
+  Modern single particle tracking approaches have taken researchers beyond
+  continuum modeling allowing them to characterize complex diffusive
+  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
+  molecular dynamics (MD) simulations to study both single particle dynamics
+  and bulk transport properties with atomic-level
+  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
+  approaches facilitate generation of hypotheses about the molecular origins of
+  separations by attempting to give a more intuitive understanding of how
+  solutes move as a function of their environment, in turn suggesting
+  experiments that could be performed.
+
+  Using a bottom-up modeling approach, we can parameterize single particle
+  behavior by extracting their trajectories from MD simulations and studying
+  the properties that have the greatest influence on solute dynamics. With this
+  information, we can learn how to construct an ensemble of characteristic
+  single solute trajectories with these properties which would be useful for
+  making long timescale predictions with computational ease and lower
+  uncertainties. Fortunately, there is an abundance of information encoded in
+  the complex solute trajectories. Into a model, we can incorporate fluctuations and
+  time-dependent correlations in solute position as well as the length of time
+  solutes are trapped. We can add further detail by integrating
+  this time series analysis with our knowledge of the primary trapping
+  mechanisms as well as the solute's changing chemical environment within the
+  heterogeneous membrane.
+
+  In this work, we use the output of our MD simulations to construct two
+  classes of mathematical models which aim to predict membrane performance
+  while providing quantitative mechanistic insights. The functional forms of
+  these models are driven by mechanistic observations from our previous work and
+  their inputs are parameterized using a substantial amount of data generated
+  by long ($\geq 5~\mu$s) MD simulations.
+
+  We constructed our first model by applying the rigorous theoretical
+  foundation already developed to describe the motion of particles exhibiting
+  non-Brownian, or anomalous, transport
+  behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
+  introduced by fractional calculus are instrumental to this
+  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
+  normally linear diffusion equation to fractional derivative orders, providing
+  descriptions of a much more diverse set of behavior, including subdiffusion,
+  a type of anomalous diffusion exhibited by solutes in this
+  study.~\cite{klages_anomalous_2008}
 
   Three well-known classes of behavior leading to anomalous subdiffusion are
-  continuous time random walks (CTRW), fractional Brownian motion
-  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
-  These types of motion are frequently used alone or in combination to describe
-  single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
-  A CTRW is characterized by a distribution of hop lengths and dwell times, 
-  where trajectories are characterized by sequential independent random draws from 
-  each distribution.\cite{montroll_random_1965} FBM is common in crowded,
+  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
+  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
+  motion are frequently used alone or in combination to describe single
+  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
+  is characterized by a distribution of hop lengths and dwell times, where
+  trajectories consist of sequential independent random draws from each
+  distribution.\cite{montroll_random_1965} FBM is common in crowded,
   viscoelastic environments where each jump comes from a Gaussian distribution
-  but is anti-correlated to its previous step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
-  An RWF is imposed by a system's geometry. Systems with tortuous pathways 
-  and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
-
-  We treated our system as an FBM process subordinate to a CTRW, or subordinated 
-  FBM (sFBM) for short. We fit sFBM
-  models in two ways: First, we parameterized solute motion using a single set of parameters fit
-  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
-  by extracting two sets of model parameters calculated based on a solute's radial
-  distance from the closest pore center. This allows us to include different dynamical
-  behavior of solutes observed within the pore region versus within the monomer tails.
-
-  Where applicable, the sFBM model provides a way to propagate information about
-  solute trajectories gathered at the microsecond time scale to realistic experimental
-  time scales. It can also confirm the importance of assumed solute-membrane interactions
-  used to define the model's functional form, and suggest missing components. It
-  can help researchers formulate hypotheses to explain why a certain set of parameters
-  is characteristic to a specific solute.
-
-  If one has knowledge of the primary mechanisms leading to anomalous diffusion behavior,
-  one may gain additional insight by formulating a state-based model, such as Markov state
-  models (MSMs). MSMs are a popular class of models used to project long timescale
-  system properties based on molecular simulation trajectories by identifying
-  different dynamical modes and quantifying the rates of transitions between them.
-  MSMs are frequently used to study systems with slow dynamics, such as protein 
-  folding.~\cite{snow_how_2005,chodera_automatic_2007} Researchers typically aim to 
-  come up with a low dimensional representation of the system based on features 
-  which preserve the process kinetics. This still often results in hundreds to thousands
-  of distinct states.~\cite{chodera_markov_2014}
-
-  Our second modeling approach applies an extended MSM framework to a relatively 
-  small set of known states based on the three previously observed solute trapping mechanisms.  
-  Standard MSMs are typically applied to determine equilibrium populations
-  of states and the kinetics of transitions between those states.~\cite{bowman_using_2009} 
-  We extend the framework to include state-dependent fluctuations and correlations in 
-  solute position. The magnitude of solute fluctuations from its average trapped 
-  position and the degree of correlation with previous fluctuations is 
-  determined by the current state. To distinguish our approach from standard MSMs, we have
-  named it the Markov state-dependent dynamical model (MSDDM).
-
-  We determine the degree of success of our modeling approaches in two ways. First,
-  if we can closely reproduce solute MSDs measured from MD simulations with realizations
-  of our models, then it is likely that the model sufficiently captures solute 
-  dynamics and can be used in a predictive capacity. Even if a model fails to 
-  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
-  The second measure of success is by analysis of the parameters defining each 
-  model. The parameters themselves should provide clues that help explain solute 
-  dynamics in a coherent way. A model that successfully reproduces MD MSDs, but 
-  with nonsensical parameters has severely diminished value as it could be a 
-  consequence of over-fitting.
-
-  The goal of this work is not to definitively determine which modeling approach
-  is better but to evaluate their performance independently because they both
-  have potential value dependent on a given research study's goals. The anomalous subdiffusion
-  approach provides a systematic way to compare the dynamical behavior of different
-  solutes based solely on the time series of their center of mass positions. The process
-  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
-  since it requires a thorough analysis of solute time series behavior. One can simulate
-  different solutes, compare the fit model parameters and relate them back to 
-  differences in solute size and chemical composition. 
-  %MRS8: this may be a bit of a stretch, since it's not clear it helps that much in the end, but 
-  %is fine to leave in now - maybe we revisit if needed during revisions.
-  The MSDDM characterizes 
-  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
-  while in each trapped state as well as the equilibrium occupation of each trapping state.
-  It is possible to use the two models in tandem, the anomalous diffusion model to
-  identify mechanisms, and the MSDDM to characterize mechanisms.
-
-  We evaluate the two modeling approaches by using them to characterize the dynamical
-  behavior of the four fastest moving solutes studied in our previous work:
-  methanol, urea, ethylene glycol and acetic acid. In addition
-  to moving quickly, allowing them to extensively explore membrane structural space,
-  these solutes have a range of chemical functionality and experience each of the 
-  three trapping mechanisms to different extents.
-
-  Finally, we use both models in order to predict solute flux and selectivity in 
-  pores of macroscopic length, thus achieving a better understanding
-  of macroscopic properties on the basis of microscopic dynamics. We show that 
+  but is anti-correlated to its previous
+  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
+  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
+  dead ends cause anti-correlated
+  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
+
+  We treated our system as an FBM process subordinate to a CTRW, or
+  subordinated FBM (sFBM) for short. We fit sFBM models in two ways: First, we
+  parameterized solute motion using a single set of parameters fit to a
+  hypothesized anomalous diffusion (AD) model. Second, we used a two-state approach
+  by extracting two sets of model parameters calculated based on a solute's
+  radial distance from the closest pore center. This allows us to include
+  different dynamical behavior of solutes observed within the pore region
+  versus within the monomer tails.
+
+  Where applicable, the sFBM model provides a way to propagate information
+  about solute trajectories gathered at the microsecond time scale to realistic
+  experimental time scales. It can also confirm the importance of assumed
+  solute-membrane interactions used to define the model's functional form, and
+  suggest missing components. It can help researchers formulate hypotheses to
+  explain why a certain set of parameters is characteristic to a specific
+  solute.
+
+  If one has knowledge of the primary mechanisms leading to anomalous diffusion
+  behavior, one may gain additional insight by formulating a state-based model,
+  such as Markov state models (MSMs). MSMs are a popular class of models used
+  to project long timescale system properties based on molecular simulation
+  trajectories by identifying different dynamical modes and quantifying the
+  rates of transitions between them. MSMs are frequently used to study systems
+  with slow dynamics, such as protein
+  folding.~\cite{snow_how_2005,chodera_automatic_2007} Researchers typically
+  aim to come up with a low dimensional representation of the system based on
+  features which preserve the process kinetics. This still often results in
+  hundreds to thousands of distinct states.~\cite{chodera_markov_2014}
+
+  Our second modeling approach applies an extended MSM framework to a
+  relatively small set of known states based on the three previously observed
+  solute trapping mechanisms. Standard MSMs are typically applied to determine
+  equilibrium populations of states and the kinetics of transitions between
+  those states.~\cite{bowman_using_2009} We extend the framework to include
+  state-dependent fluctuations and correlations in solute position. The
+  magnitude of a solute's fluctuations from its average trapped position and the
+  degree of correlation with previous fluctuations is determined by the current
+  state. To distinguish our approach from standard MSMs, we have named it the
+  Markov state-dependent dynamical model (MSDDM).
+
+  We determine the degree of success of our modeling approaches in two ways.
+  First, if we can closely reproduce solute MSDs measured from MD simulations
+  with realizations of our models, then it is likely that the model
+  sufficiently captures solute dynamics and can be used in a predictive
+  capacity. Even if a model fails to reproduce the MD MSDs, there is value in
+  uncovering the cause of the deviation. 
+  %BJC9: I modified the following from the commented out version below it in order to be more consistent with what we actually did.
+  The second measure of success is based on the qualitative comparison between
+  individual realizations of solute trajectories generated by our models and
+  those observed from MD simulations. Even if we can reproduce the solute MSDs
+  based on realizations of our models, the absence or inappropriate
+  reproduction of hopping and trapping behavior may indicate underlying model
+  issues. 
+  %The second measure of success is by
+  %analysis of the parameters defining each model. The parameters themselves
+  %should provide clues that help explain solute dynamics in a coherent way. A
+  %model that successfully reproduces MD MSDs, but with nonsensical parameters
+  %has severely diminished value as it could be a consequence of over-fitting.
+
+  The goal of this work is not to definitively determine which modeling
+  approach is better but to evaluate their performance independently because
+  they both have potential value dependent on a given research study's goals.
+  The AD approach provides a systematic way to compare the dynamical behavior
+  of different solutes based solely on the time series of their center of mass
+  positions. The process of choosing the correct AD approach provides its own
+  mechanistic insight since it requires a thorough analysis of solute time
+  series behavior. One can simulate different solutes, compare the fit model
+  parameters and relate them back to differences in solute size and chemical
+  composition. The MSDDM characterizes explicitly defined trapping mechanisms,
+  providing a clear picture of solute behavior while in each trapped state as
+  well as the equilibrium occupation of each trapping state.  It is possible to
+  use the two modelling approaches in tandem, the AD approach to identify
+  mechanisms, and the MSDDM to characterize mechanisms.
+
+  We evaluate the two modeling approaches by using them to characterize the
+  dynamical behavior of the four fastest moving solutes studied in our previous
+  work: methanol, urea, ethylene glycol and acetic acid. In addition to moving
+  quickly, allowing them to extensively explore membrane structural space,
+  these solutes have a range of chemical functionality and experience each of
+  the three trapping mechanisms to different extents.
+
+  Finally, we use both models in order to predict solute flux and selectivity
+  in pores of macroscopic length, thus achieving a better understanding of
+  macroscopic properties on the basis of microscopic dynamics. We show that
   anti-correlated solute hopping behavior severely reduces flux relative to
   uncorrelated behavior. We use the relative solute fluxes to estimate the
-  membrane's selectivity between all pairs of solutes and demonstrate that, when 
-  solutes display different degrees of anti-correlated hopping behavior, selectivity
-  becomes a function of pore length. With this improved understanding of 
-  macroscopic behavior, we can begin to think more critically about how to design 
-  membranes in order to selectively pass or reject specific solutes.
+  membrane's selectivity between all pairs of solutes and demonstrate that,
+  when solutes display different degrees of anti-correlated hopping behavior,
+  selectivity becomes a function of pore length. With this improved
+  understanding of macroscopic behavior, we can begin to think more critically
+  about how to design membranes in order to selectively pass or reject specific
+  solutes.
 
@@
 
-  We ran all MD simulations and energy minimizations using GROMACS 2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
-%BJC4: version 2018.
-That's it not 2018.3 or anything.
-  We performed all post-simulation trajectory analysis using Python scripts which 
-  are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
-  The appropriate scripts to use for subsequent calculations are summarized in 
+  We ran all MD simulations and energy minimizations using GROMACS
+  2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
+  We performed all post-simulation trajectory analysis using Python scripts
+  which are available online at \\
+  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.  The appropriate
+  scripts to use for subsequent calculations are summarized in
   Table~\ref{S-table:python_scripts} of the Supplemental Material.
@@
 
-  We studied transport of solutes in the H\textsubscript{II} phase using an atomistic
-  molecular model of four pores in a monoclinic unit cell with 10\% water by weight 
-  (see Figure~\ref{fig:membrane_structure}). Approximately one third of the water 
-  molecules occupy the tail region with the rest near the pore center. We chose to
-  focus our study on the 10 wt\% water system because solutes move significantly 
-  faster than in the 5 wt\% system studied previously thus allowing more statistically
-  valid analyses.
+  We studied transport of solutes in the H\textsubscript{II} phase using an
+  atomistic molecular model of four pores in a monoclinic unit cell with 10\%
+  water by weight (see Figure~\ref{fig:membrane_structure}). Approximately one
+  third of the water molecules occupy the tail region with the rest near the
+  pore center. We chose to focus our study on the 10 wt\% water system because
+  solutes move significantly faster than in the 5 wt\% system studied
+  previously, thus allowing more statistically valid analyses.
 
@@
   dynamic behavior of solute trajectories. Rather than using them to calculate 
-  diffusion constants or to relate our simulations to experimental measurement, we
+  diffusion constants or to relate our simulations to experimental measurements, we
   compare MSDs calculated from MD simulations to those generated from our models 
@@
   \end{equation}
-  Fits to the \textit{ensemble} averaged MSD will always reproduce the form of 
+  Fits to the ensemble averaged MSD will always reproduce the form of 
   Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
@@
 
-  We chose to use just the time-averaged MSD to compare MD trajectory and modeled
-  trajectories, because, compared to the ensemble average, it is a more 
-  statistically robust measure of the average distance a solute travels over time.
-  The ensemble MSD of only 24 solute trajectories would have much higher uncertainties.
+  We chose to use just the time-averaged MSD to compare MD trajectories with
+  modeled trajectories, because, compared to the ensemble average, it is a more
+  statistically robust measure of the average distance a solute travels over
+  time. The ensemble MSD of only 24 solute trajectories would have much higher
+  uncertainties.
 
@@
 
-  One can characterize the CTRW component of an sFBM process by the parameters which describe
-  its dwell time and hop length distributions. We used the \texttt{ruptures} Python
-  package in order to automatically identify mean shifts in solute trajectories, 
-  indicating hops.\cite{truong_ruptures:_2018} We used the corresponding hop lengths
-  and dwell times between hops to construct empirical distributions.
+  One can characterize the CTRW component of an sFBM process by the parameters
+  which describe its dwell time and hop length distributions. We used the
+  \texttt{ruptures} Python package in order to automatically identify mean
+  shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018}
+  We used the corresponding hop lengths and dwell times between hops to
+  construct empirical distributions.
 
@@
 
-  \textit{Correlated hop length distributions:} The marginal distribution of hop 
+  \textit{Correlated hop length distributions:} The distribution of hop 
   lengths by solutes undergoing an sFBM process is Gaussian, therefore we 
@@
 
-  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
-  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
+  sFBM implies that hops are correlated which we describe using the Hurst
+  parameter, $H$. The autocovariance function of hop lengths has the
+  analytical form:~\cite{mandelbrot_fractional_1968}
   \begin{equation}
@@
   \end{equation}
-  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
-  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
-  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
-  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
-  and when $H > 0.5$, one observes positive correlation between hops.
+  where $\sigma^2$ is the variance of the underlying Gaussian distribution from
+  which hops are drawn and $k$ is the time lag, or number of increments between
+  hops. The hop autocorrelation function is simply
+  Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance.  When $H <
+  0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian
+  motion and when $H > 0.5$, one observes positive correlation between hops.
 
@@
 
-  Because we also want to account for the possibility that distribution of hops is 
-  not Gaussian, we can model them with the more general class of L\'evy stable 
-  distributions. For independent and identically distributed random variables, 
-  the generalized central limit theorem assures convergence of the associated 
-  probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
-  The characteristic equation which describes the Fourier transform of a L\'evy stable PDF is: 
+  Because we also want to account for the possibility that the distribution of
+  hops is not Gaussian, we can model them with the more general class of L\'evy
+  stable distributions. For independent and identically distributed random
+  variables, the generalized central limit theorem assures convergence of the
+  associated probability distribution function (PDF) to a L\'evy stable PDF.
+  \cite{klages_anomalous_2008} The characteristic equation which describes the
+  Fourier transform of a L\'evy stable PDF is: 
   \begin{equation}
@@
   For correlated hops, solute behavior may be described by subordinated
-  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to describe
-  hop correlations because they share the same autocorrelation structure.~\cite{tikanmaki_fractional_2010}
-  The autocovariance function for FLM is:
+  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to
+  describe hop correlations because they share the same autocorrelation
+  structure.~\cite{tikanmaki_fractional_2010} The autocovariance function for
+  FLM is:
   \begin{equation}
@@
 
-  Analogous to power law dwell times, the heavy tails of L\'evy stable hop length 
-  distributions result in rare but arbitrarily long hops. These long and unrealistic
-  hops result in over-estimated simulated MSDs (see Figure~\ref{fig:ad_realizations_1mode}
-  for example). We observe that the distribution of hops observed in our MD simulations
-  are well approximated by L\'evy stable distributions close to the mean, but they 
-  significantly under-sample the tails. We chose to truncate the L\'evy stable distributions
-  based on where the theoretical probability distribution function (PDF) starts to 
-  deviate from the empirically measured PDF (see Section~\ref{S-section:truncation}
-  of the Supplemental Material).~\cite{mantegna_stochastic_1994}
+  Analogous to power law dwell times, the heavy tails of L\'evy stable hop
+  length distributions result in rare but arbitrarily long hops. These long and
+  unrealistic hops result in over-estimated simulated MSDs (see
+  Figure~\ref{fig:ad_realizations_1mode} for example). We observe that the
+  distribution of hops observed in our MD simulations are well approximated by
+  L\'evy stable distributions close to the mean, but they significantly
+  under-sample the tails. We chose to truncate the L\'evy stable distributions
+  based on where the theoretical probability distribution function (PDF) starts
+  to deviate from the empirically measured PDF (see
+  Section~\ref{S-section:truncation} of the Supplemental
+  Material).~\cite{mantegna_stochastic_1994}
 
@@
 
-  We observe different dynamical behavior when solutes move while inside 
-  the pore versus while in the tail region. This suggest two anomalous diffusion 
-  models of varying complexity. We first create a simple, single mode model with
-  a single set of parameters fit to solute trajectories.
-  Our second, two mode model assigns a set of parameters to each of 2 modes based
-  on the solute's radial location. We define the first mode as the pore region, 
+  We observe different dynamical behavior when solutes move while inside the
+  pore versus while in the tail region. This suggests two anomalous diffusion
+  models of varying complexity. We first create a simple, single mode model
+  with a single set of parameters fit to solute trajectories. Our second, two
+  mode model assigns a set of parameters to each of 2 modes based on the
+  solute's radial location. We define the first mode as the pore region,
   defined as less than 0.75 nm from any pore center. Solutes outside the pore
   region are in the second mode, the tail region. We determined this cut-off by
-  maximizing the difference in dynamical behavior as 
-  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
-  there were not enough sufficiently long sequences of hops in each mode to reliably
-  calculate a Hurst parameter for each mode so we used the single, average Hurst 
-  parameter from the single mode model for both modes of the two mode model.
+  maximizing the difference in dynamical behavior as described in our previous
+  work.~\cite{coscia_chemically_2019} Unfortunately, there were not enough
+  sufficiently long sequences of hops in each mode to reliably calculate a
+  Hurst parameter for each mode so we used the single, average Hurst parameter
+  from the single mode model for both modes of the two mode model.
 
   For the two mode model, we defined a transition matrix describing the rate at
-  which solutes moved between the tail and pore region. We assumed Markovian transitions
-  between modes, meaning each transition had no memory of previously visited modes. 
-  We populated a 2$\times$2 count matrix by incrementing the appropriate entry by 1 
-  each time step and then generated a transition probability matrix by normalizing 
-  the entries in each row of the count matrix so that they summed to unity.
+  which solutes moved between the tail and pore region. We assumed Markovian
+  transitions between modes, meaning each transition had no memory of
+  previously visited modes. We populated a 2$\times$2 count matrix by
+  incrementing the appropriate entry by 1 each time step and then generated a
+  transition probability matrix by normalizing the entries in each row of the
+  count matrix so that they summed to unity.
 
@@
       Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
-	  %\hline
+	  \hline
+          \hline
 	  \end{tabular}
 	  \caption{We tested four anomalous diffusion models with various modifications 
-	  to the dwell and hop length distributions. We incorporate correlation structure
+	  to the dwell and hop length distributions. We incorporate hop correlation 
 	  into all models.}\label{table:anomalous_models}
+
  \end{table}
 
-  For each solute, we simulated 1,000 anomalous diffusion trajectories of length
-  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
-  $T_{sim}$ varied between solutes due to differing solute equilibration times. We constructed 
-  trajectories by simulating sequences of dwell times and correlated hop lengths
-  generated based on parameters randomly chosen from our bootstrapped parameter 
-  distributions. We propagated each trajectory until the total time equaled or 
-  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
-  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
-  between fixed length sFBM simulations.
+  For each solute, we simulated 1,000 anomalous diffusion trajectories of
+  length $T_{sim}$ in order to directly compare our model's predictions to MD
+  simulations. $T_{sim}$ varied between solutes due to differing solute
+  equilibration times. We constructed trajectories by simulating sequences of
+  dwell times and correlated hop lengths generated based on parameters randomly
+  chosen from our bootstrapped parameter distributions. We propagated each
+  trajectory until the total time equaled or exceeded $T_{sim}~ \mu$s, then
+  truncated the last data point so that the total time exactly equaled
+  $T_{sim}~ \mu$s since valid comparisons are only possible between fixed
+  length sFBM simulations.
 
@@
   and AD model trajectories then estimated their uncertainty using statistical
-  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute trajectories,
-  where $n$ is the number of independent trajectories, with replacement, from the 
-  ensemble of trajectories and then calculated the MSD of the subset. We reported 
-  the time-averaged MSD up to a 1000 ns time lag with corresponding 1$\sigma$ confidence
-  intervals.
-
-  When simulating 2 mode models, we determined the state sequence based on random 
-  draws weighted by the appropriate row of the probability transition matrix. We then
-  drew hops and dwells based on the current state of the system. Since we calculated
-  the transition probabilities from a finite data set, they have an associated 
-  uncertainty which we incorporated by re-sampling each row from a two dimensional
-  Dirichlet distribution (which is also a beta distribution for the 2D case) with 
-  concentration parameters defined by the count matrix.~\cite{bacallado_bayesian_2009}
+  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute
+  trajectories, where $n$ is the number of independent trajectories, with
+  replacement, from the ensemble of trajectories and then calculated the MSD of
+  the subset. We reported the time-averaged MSD up to a 1000 ns time lag with
+  corresponding 1$\sigma$ confidence intervals.
+
+  When simulating 2 mode models, we determined the state sequence based on
+  random draws weighted by the appropriate row of the probability transition
+  matrix. We then drew hops and dwells based on the current state of the
+  system. Since we calculated the transition probabilities from a finite data
+  set, they have an associated uncertainty which we incorporated by re-sampling
+  each row from a two dimensional Dirichlet distribution (which is also a beta
+  distribution for the 2D case) with concentration parameters defined by the
+  count matrix.~\cite{bacallado_bayesian_2009}
 
   %BJC3: not sure how to cite fbm
-  We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
-  own Python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
-  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
-  simulation algorithms for generating FLM trajectories. However, the algorithm
-  we used sufficiently approximates draws from the marginal distribution and 
-  reasonably approximates the correlation structure on MD simulation timescales. We
-  added an empirical correction to enhance the accuracy of the correlation structure
-  (see Section~\ref{S-section:flm_correlation} of the Supplemental Material for 
+  %TODO: cite github page for fbm
+  We used the Python package \texttt{fbm} to generate exact simulations of FBM
+  and our own Python implementation of the algorithm by Stoev and Taqqu to
+  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
+  are no known exact simulation algorithms for generating FLM trajectories.
+  However, the algorithm we used sufficiently approximates draws from the
+  marginal L\'evy stable distribution and reasonably approximates the
+  correlation structure on MD simulation timescales. We added an empirical
+  correction to enhance the accuracy of the correlation structure (see
+  Section~\ref{S-section:flm_correlation} of the Supplemental Material for
   validation of the approach).
@@
 
-  A Markov state model (MSM) decomposes a time series into a set of discrete states
-  with transitions between states defined by a transition probability matrix, $T$,
-  which describes the conditional probability of moving to a specific state given
-  the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
-  %MRS6: maybe skip this next sentence since you don't actually use them?
+  A Markov state model (MSM) decomposes a time series into a set of discrete
+  states with transitions between states defined by a transition probability
+  matrix, $T$, which describes the conditional probability of moving to a
+  specific state given the previously observed
+  state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
 %  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
@@
   apply any algorithmic approaches to identify and decompose our system into
-  discrete states. The states we have chosen include all combinations of trapping
-  mechanisms in the pore and out of the pore (see Table~\ref{table:states}). They
-  assume that there are no significant kinetic effects resulting from solute 
-  conformational changes or pore size fluctuations. We use the same radial cut-off
-  (0.75 nm) as in the AD model to differentiate the pore and tail region.  We define 
-  a hydrogen bond to exist if the distance between donor, D, and acceptor, A, 
-  atoms is less than 3.5 \AA~and the angle formed by $D-H \cdots A$ is less than
+  discrete states. The states we have chosen include all combinations of
+  trapping mechanisms in the pore and out of the pore (see
+  Table~\ref{table:states}). They assume that there are no significant kinetic
+  effects resulting from solute conformational changes or pore size
+  fluctuations. We use the same radial cut-off (0.75 nm) as in the AD approach to
+  differentiate the pore and tail region. We define a hydrogen bond to exist
+  if the distance between donor, D, and acceptor, A, atoms is less than 3.5
+  \AA~and the angle formed by $D-H \cdots A$ is less than
   30$\degree$.~\cite{luzar_effect_1996} We define a sodium ion to be associated
@@
 
-  %BJC8: reformatted. I think this is what they want in terms of format
   \begin{table}[!htb]
@@
 
-  We constructed the state transition probability matrix, $T$, based on observed 
-  solute trajectories. Using methods described in our previous work, we determined 
-  each solute's radial location and which, if any, trapping mechanisms affected 
-  it at each time step, then assigned the observation to a specific state according
-  to the definitions in Table~\ref{table:states}.~\cite{coscia_chemically_2019}
-  Analogous to the mode transition matrix in Section~\ref{method:model_sFBM}, and 
-  based on the current and previous state observation, we incremented the appropriate
-  entry of an $n~\times~n$ count matrix by 1, where $n$ is the number of states. We
+  We constructed the state transition probability matrix, $T$, based on
+  observed solute trajectories. Using methods described in our previous work,
+  we determined each solute's radial location and which, if any, trapping
+  mechanisms affected it at each time step, then assigned the observation to a
+  specific state according to the definitions in
+  Table~\ref{table:states}.~\cite{coscia_chemically_2019} Analogous to the mode
+  transition matrix in Section~\ref{method:model_sFBM}, and based on the
+  current and previous state observation, we incremented the appropriate entry
+  of an $n~\times~n$ count matrix by 1, where $n$ is the number of states. We
   verified the Markovianity of state transitions as described in
@@
 
-  Adding to the standard MSM framework, we incorporated the dynamics of the solutes
-  within each state as well as the dynamics of state transitions, which includes the
-  overall configurational state of the solute and it's environments. 
-  While MSMs are often used to estimate equilibrium populations of various states, adding 
-  state-dependent dynamics allows us to simulate solute trajectories.
-  %BJC5: I said the following earlier , but I still think it belongs
-  Hence why we refer to them as Markov state-dependent dynamical models (MSDDMs).
-
-  We recorded the $z$-direction displacement at each time step in order to construct 
-  individual emission distributions for each state and transition between states. 
-  This results in 64 distinct emission distributions with some far more populated than
-  others. We modeled all of the emission distributions as symmetric L\'evy stable 
-  distributions in order to maintain flexibility in parameterizing the distributions.
-
-  We use the Hurst parameter to describe this negative time series correlation.
-  However, there is not sufficient data to accurately measure a Hurst parameter for 
-  each type of transition. We avoided this problem by combining all distributions 
-  associated with state transitions and treating all transitions as correlated
-  emissions from a single L\'evy stable distribution. This reduces the number of emission
-  distributions from 64 to 9 (1 for each of the 8 states and 1 for transitions between states).
-
-  We simulated realizations of the MSDDM using the probability transition matrix and 
-  emission distributions. For each trajectory simulated, we chose an initial state
-  randomly from a uniform distribution. We generated a full state sequence by randomly
-  drawing subsequent states weighted by the rows of the probability transition matrix
-  corresponding to the particle's current state. Again, because we are working with a
-  finite data set, we incorporated transition probability uncertainties into the rows
-  of the transition matrix by resampling them from a Dirichlet distribution. For each 
-  same-state subsequence of the full state sequence, we simulated an FLM process using
-  the Hurst parameter of that state and the parameters of the corresponding emission
-  distribution. Independently, we simulated the transition between each same-state 
-  sequence with an FLM process based on the Hurst parameter of transition sequences 
-  and the parameters of the single transition emission distribution. We used the same
-  FLM simulation procedure described in Section~\ref{method:model_sFBM}.
+  Adding to the standard MSM framework, we incorporated the dynamics of the
+  solutes within each state as well as the dynamics of state transitions, which
+  includes the overall configurational state of the solute and it's
+  environments. While MSMs are often used to estimate equilibrium populations
+  of various states, adding state-dependent dynamics allows us to simulate
+  solute trajectories. Hence why we refer to them as Markov state-dependent
+  dynamical models (MSDDMs).
+
+  We recorded the $z$-direction displacement at each time step in order to
+  construct individual emission distributions for each state and transition
+  between states. This results in 64 distinct emission distributions with some
+  far more populated than others. We modeled all of the emission distributions
+  as symmetric L\'evy stable distributions in order to maintain flexibility in
+  parameterizing the distributions.
+
+  We use the Hurst parameter to describe negative time series correlation.
+  However, there is not sufficient data to accurately measure a Hurst parameter
+  for each type of transition. We avoided this problem by combining all
+  distributions associated with state transitions and treating all transitions
+  as correlated emissions from a single L\'evy stable distribution. This
+  reduces the number of emission distributions from 64 to 9 (1 for each of the
+  8 states and 1 for transitions between states).
+
+  We simulated realizations of the MSDDM using the probability transition
+  matrix and emission distributions. For each trajectory simulated, we chose an
+  initial state randomly from a uniform distribution. We generated a full state
+  sequence by randomly drawing subsequent states weighted by the rows of the
+  probability transition matrix corresponding to the particle's current state.
+  Again, because we are working with a finite data set, we incorporated
+  transition probability uncertainties into the rows of the transition matrix
+  by resampling them from a Dirichlet distribution. For each same-state
+  subsequence of the full state sequence, we simulated an FLM process using the
+  Hurst parameter of that state and the parameters of the corresponding
+  emission distribution. Independently, we simulated the transition between
+  each same-state sequence with an FLM process based on the Hurst parameter of
+  transition sequences and the parameters of the single transition emission
+  distribution. We used the same FLM simulation procedure described in
+  Section~\ref{method:model_sFBM}.
 
@@
 
-  We determine the rate at which solutes cross macroscopic-length pores based on the
-  Hill relation:~\cite{hill_free_1989}
+  We determine the rate at which solutes cross macroscopic-length pores based
+  on the Hill relation:~\cite{hill_free_1989}
   \begin{equation}
@@
   \end{equation}
-  where $J$ is the single particle solute flux and MFPT refers to the mean first passage
-  time. To account for input concentration dependence of the flux, assuming that particles
-  are independent, one can multiply Equation~\ref{eqn:hill_relation} by the total number
-  of particles to get the total flux. In the context of our work, the MFPT describes the
-  average length of time it takes a particle to move from the pore entrance to the pore exit.
-
-  We generated particle trajectories, parameterized with the above models, in order
-  to construct a distribution of first passage times across a membrane pore of length $L$.
-  For each pore length, we simulated 10,000 realizations of the AD model
+  where $J$ is the single particle solute flux and MFPT refers to the mean
+  first passage time. To account for input concentration dependence of the
+  flux, assuming that particles are independent, one can multiply
+  Equation~\ref{eqn:hill_relation} by the total number of particles to get the
+  total flux. In the context of our work, the MFPT describes the average length
+  of time it takes a particle to move from the pore entrance to the pore exit.
+
+  We generated particle trajectories, parameterized with the above models, in
+  order to construct a distribution of first passage times across a membrane
+  pore of length $L$. For each pore length, we simulated 10,000 realizations
+  of an AD approach model
   % and, due to 
   %computational costs, 1,000 realizations of the MSDDM, 
-  all released at the pore entrance ($z=0$).
-  In the case of uncorrelated hops, one can continuously draw from the hop length 
-  distribution until $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
-  between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
-  single passage time. When particle hops are correlated, as they are in all cases of
-  this work, we cannot continuously construct the particle trajectories. Rather, we must
-  generate trajectories of length $n$ and measure the length of the sub-trajectory 
-  which traverses from $0$ to $L$ without becoming negative.
-
-  We calculated the expected value of analytical fits to the passage time distributions
-  in order to determine the MFPT for a given solute and pore length. One should not 
-  use the mean of the empirical passage time distribution because it is highly likely
-  that the true MFPT will be underestimated unless 100\% of a very large number of 
-  trajectories reach $L$. If a trajectory does not reach $L$ within $n$ steps, it is
-  possible that a very long passage time has been excluded from the distribution.
+  all released at the pore entrance ($z=0$).  In the case of uncorrelated hops,
+  one can continuously draw from the hop length distribution until $z \geq L$
+  (or $-L$ for the sake of computational efficiency). The length of time
+  between the last time the particle crossed $z=0$ and the end of the
+  trajectory gives a single passage time. When particle hops are correlated, as
+  they are in all cases of this work, we cannot continuously construct the
+  particle trajectories. Rather, we must generate trajectories of length $n$
+  and measure the length of the sub-trajectory which traverses from $0$ to $L$
+  without becoming negative.
+
+  We calculated the expected value of analytical fits to the passage time
+  distributions in order to determine the MFPT for a given solute and pore
+  length. One should not use the mean of the empirical passage time
+  distribution because it is highly likely that the true MFPT will be
+  underestimated unless 100\% of a very large number of trajectories reach $L$.
+  If a trajectory does not reach $L$ within $n$ steps, it is possible that a
+  very long passage time has been excluded from the distribution.
 
   To derive an analytical equation describing the passage time distributions,
-  one can frame the 
-  problem as a pulse of particles instantaneously released at the pore inlet ($z=0$)
-  which moves at a constant velocity, $v$, and spreads out as it approaches $L$. 
-  This spreading is parameterized by an effective diffusivity parameter, $D$. This 
-  approach gives results equivalent to if we had released each particle individually
-  and then analyzed the positions of the ensemble of trajectories as 
-  a function of time. The analytical expression describing the distribution of 
-  first passage times is:~\cite{cussler_diffusion:_2009}
+  one can frame the problem as a pulse of particles instantaneously released at
+  the pore inlet ($z=0$) which moves at a constant velocity, $v$, and spreads
+  out as it approaches $L$. This spreading is parameterized by an effective
+  diffusivity parameter, $D$. This approach gives results equivalent to if we
+  had released each particle individually and then analyzed the positions of
+  the ensemble of trajectories as a function of time. The analytical expression
+  describing the distribution of first passage times
+  is:~\cite{cussler_diffusion:_2009}
   \begin{equation}
@@
   \end{equation} 
-  where the only free parameters for fitting are $v$ and $D$. A derivation
-  of Equation~\ref{eqn:passage_times} is given in Section~\ref{S-section:fpt_derivation}
-  of the Supplemental Material. We calculated the expected value of 
-  Equation~\ref{eqn:passage_times} in order to get the MFPT.
+  where the only free parameters for fitting are $v$ and $D$. A derivation of
+  Equation~\ref{eqn:passage_times} is given in
+  Section~\ref{S-section:fpt_derivation} of the Supplemental Material. We
+  calculated the expected value of Equation~\ref{eqn:passage_times} in order to
+  get the MFPT.
   %MRS8: check to make sure there is goodness-of-fit checks in the SI for fitting to the analytical model.
-
-  We used the ratio of solute fluxes in order to determine membrane selectivity, $S_{ij}$,
-  towards solutes. Selectivity of solute $i$ versus $j$ is defined in terms of the
-  ratio of solute permeabilities, $P$:~\cite{guo_pervaporation_2004}
+  %BJC8: TODO
+
+  We used the ratio of solute fluxes in order to determine membrane
+  selectivity, $S_{ij}$, towards solutes. Selectivity of solute $i$ versus $j$
+  is defined in terms of the ratio of solute permeabilities,
+  $P$:~\cite{guo_pervaporation_2004}
   \begin{equation}
@@
   We can relate this to solute flux using Kedem and Katchalsky's equations for
-  solvent volumetric flux, $J_v$, and solute flux, $J_s$:~\cite{kedem_permeability_1963,al-zoubi_rejection_2007}
+  solvent volumetric flux, $J_v$, and solute flux,
+  $J_s$:~\cite{kedem_permeability_1963,al-zoubi_rejection_2007}
   %al-zoubi_rejection_2007 clarifies that these equations can be used for nanofiltration, ultrafiltration etc. by treating the membrane as a black box subject to irreversible thermodynamics.
@@
   \end{equation}
-  where $L_p$ is the pure water permeability, $\Delta P$ and $\Delta \pi$ are the 
-  trans-membrane hydraulic and osmotic pressure differences, $\sigma$ is the reflection
-  coefficient, $P_s$ is the solute permeability, $\Delta C$ is the trans-membrane
-  solute concentration difference and $C$ is the mean solute concentration. Since our
-  simulations do not include convective solute flux, we eliminate the second term 
-  of Equation~\ref{eqn:solute_flux} which allows us to derive a simple expression
-  for selectivity in terms of solute flux:
+  where $L_p$ is the pure water permeability, $\Delta P$ and $\Delta \pi$ are
+  the trans-membrane hydraulic and osmotic pressure differences, $\sigma$ is
+  the reflection coefficient, $P_s$ is the solute permeability, $\Delta C$ is
+  the trans-membrane solute concentration difference and $C$ is the mean solute
+  concentration. Since our simulations do not include convective solute flux,
+  we eliminate the second term of Equation~\ref{eqn:solute_flux} which allows
+  us to derive a simple expression for selectivity in terms of solute flux:
   \begin{equation}
@@
 
-  We find the data suggests that solute motion in this system can be well-modeled by 
-  subordinated fractional Brownian motion. In Figure~\ref{fig:solute_trajectories},
-  we plotted representative trajectories for each solute. They are characterized 
-  by intermittent hops between periods of entrapment. The near-Gaussian distribution
-  of jump lengths and power law distribution of dwell times are both characteristic
-  of CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). 
-  The apparent anti-correlation between hops suggests a fractional diffusion process
-  is subordinate to the CTRW. Of the different models, a process subordinated by FBM
-  or FLM is best supported by the data because the analytical correlation structures
-  of hop lengths are close to those observed in our simulations (Figure~\ref{fig:hop_acf}).
-  Fractional motion is common in crowded viscoelastic environments where movement is
-  highly influenced by the movement of surrounding components, such as monomer tails 
-  in our case.~\cite{ernst_fractional_2012}
+  We find the data suggests that solute motion in this system can be
+  well-modeled by subordinated fractional Brownian motion. In
+  Figure~\ref{fig:solute_trajectories}, we plotted representative trajectories
+  for each solute. They are characterized by intermittent hops between periods
+  of entrapment. The near-Gaussian distribution of jump lengths and power law
+  distribution of dwell times are both characteristic of CTRWs
+  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}).  The
+  apparent anti-correlation between hops suggests a fractional diffusion
+  process is subordinate to the CTRW. Of the different models, a process
+  subordinated by FBM or FLM is best supported by the data because the
+  analytical correlation structures of hop lengths are close to those observed
+  in our simulations (Figure~\ref{fig:hop_acf}). Fractional motion is common
+  in crowded viscoelastic environments where motion is highly influenced by
+  the movement of surrounding components, such as monomer tails in our
+  case.~\cite{ernst_fractional_2012}
 
@@
   \caption{Representative trajectories generated from each solute exhibit hops
-  between periods of entrapment, characteristic of a CTRW. Solute dynamics show
-  radial dependence, represented by the color at each time point. The longest 
-  periods of entrapment typically occur when solutes drift far from the pore 
-  center and into the tails.
+	  between periods of entrapment, characteristic of a CTRW. Solute
+	  dynamics show radial dependence, represented by the color at each
+	  time point. The longest periods of entrapment typically occur when
+	  solutes drift far from the pore center and into the tails.
   }\label{fig:solute_trajectories}
@@
   \end{subfigure}
-  \caption{Using urea as an example, (a) the distribution of hop lengths can be fit by 
-  a Gaussian as well as a more general L\'evy stable distribution. The L\'evy stable
-  distribution does a better job of capturing the heavier tails and increased density
-  near 0. We explore models fit to both distributions since Gaussian hops are convenient to
-  model. (b) The distribution of dwell times is fit well by a power law but it
-  over-estimates the probability density at long dwell times. A power law truncated with
-  an exponential cut-off better describes the probability of long dwell times in 
-  our simulations. (c) The hops are negatively correlated to their previous hop. In
-  combination, (a) -- (c) support modeling solutes as either subordinated fractional
-  Brownian or L\'evy motion. All other solutes show similar distributions and autocorrelation
-  functions (see Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
+  \caption{Using urea as an example, (a) the distribution of hop lengths can be
+	  fit by a Gaussian as well as a more general L\'evy stable
+	  distribution. The L\'evy stable distribution does a better job of
+	  capturing the heavier tails and increased density near 0. We explore
+	  models fit to both distributions since Gaussian hops are convenient
+	  to model. (b) The distribution of dwell times is fit well by a power
+	  law but it over-estimates the probability density at long dwell
+	  times. A power law truncated with an exponential cut-off better
+	  describes the probability of long dwell times in our simulations. (c)
+	  The hops are negatively correlated to their previous hop. In
+	  combination, (a) -- (c) support modeling solutes as either
+	  subordinated fractional Brownian or L\'evy motion. All other solutes
+	  show similar distributions and autocorrelation functions (see
+	  Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
   }\label{fig:anticorrelated_hops}
@@
 
-  We modeled the distributions of hop lengths in two ways. First, we assumed the 
-  distribution to be Gaussian since it is possible to exactly simulate realizations of
-  fractional Brownian motion. Second, we fit the distributions to L\'evy stable 
-  distributions since it is more general than the Gaussian distribution. We plotted
-  the MLE fits of both on top of urea's hop length distribution in 
-  Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a 
-  better job capturing the somewhat heavy tails and high density near 0 of the hop
-  length distribution. However, since there are no known exact simulation techniques
-  for generating realizations of fractional L\'evy motion, this more general 
-  fit may not be worthwhile. In fact, we typically observe very little difference 
-  between model predictions parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).
-%  we must evaluate whether
-%  this more general fit is worthwhile. 
-  %MRS8: would it be better to put the decision here, or at least say where this decision is made?  Otherwise the reader has a lot of potential decisions to keep in their mind. 
-  %BJC8: probably a good idea.
-
-  We also modeled the distribution of dwell times in two ways. First, we assumed pure
-  power law behavior since it is consistent with most theoretical descriptions of CTRWs.
-  The data fits well to this model at short dwell times but the density of long dwell
-  times is over-estimated. In our second approach, we truncate the power law distribution
-  with an exponential cut-off, lowering the probability of extremely long dwell times. 
-  We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where the
-  density of the truncated power law drops below that of the pure power law and tends towards
+  We modeled the distributions of hop lengths in two ways. First, we assumed
+  the distribution to be Gaussian since it is possible to exactly simulate
+  realizations of fractional Brownian motion. Second, we fit the distributions
+  to L\'evy stable distributions since it is more general than the Gaussian
+  distribution. We plotted the MLE fits of both on top of urea's hop length
+  distribution in Figure~\ref{fig:hop_distribution_comparison}. The L\'evy
+  distribution does a better job capturing the somewhat heavy tails and high
+  density near 0 of the hop length distribution. However, since there are no
+  known exact simulation techniques for generating realizations of fractional
+  L\'evy motion, this more general fit may not be worthwhile. In fact, we
+  typically observe very little difference between model predictions
+  parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).
+
+  We also modeled the distribution of dwell times in two ways. First, we
+  assumed pure power law behavior since it is consistent with most theoretical
+  descriptions of CTRWs. The data fits well to this model at short dwell times
+  but the density of long dwell times is over-estimated. In our second
+  approach, we truncate the power law distribution with an exponential cut-off,
+  lowering the probability of extremely long dwell times. We demonstrate this
+  effect in the inset to Figure~\ref{fig:powerlaw}, where the density of the
+  truncated power law drops below that of the pure power law and tends towards
   0 near a dwell time of 250 ns.
 
-  %MRS8: be more specific than ``the AD model'' below?
-Also, not sure how clear this thesis is since you described 2x2=4 different models in the previous two paragraphs - at this point, the reader isn't sure of a single model.
-Tried a pass.
-  %Realizations of the AD model based on the parameterization procedures just described
   Several of the choices of AD models and parameters we have described yield
-  qualitatively similar trajectories to those seen in our MD simulations. 
-  In Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for each
-  combination of the dwell time and hop distribution, labeled according to Table~\ref{table:anomalous_models}.
-  The sFBMcut and sFLMcut in particular resemble the trajectories in Figure~\ref{fig:solute_trajectories}.
-  When we do not truncate the dwell time distribution, the trajectories tend to 
-  incorporate very long dwell times as shown by the sFBM and sFLM models. Predictions
-  made with these models consistently under-predict the MD MSDs (see 
-  Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supplemental Material). Therefore, 
-  we will not include the pure sFBM or sFLM models in the remainder of our analysis.
+  qualitatively similar trajectories to those seen in our MD simulations.  In
+  Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for
+  each combination of the dwell time and hop distribution, labeled according to
+  Table~\ref{table:anomalous_models}. The sFBMcut and sFLMcut in particular
+  resemble the trajectories in Figure~\ref{fig:solute_trajectories}.  When we
+  do not truncate the dwell time distribution, the trajectories tend to
+  incorporate very long dwell times as shown by the sFBM and sFLM models.
+  Predictions made with these models consistently under-predict the MD MSDs
+  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supplemental
+  Material). Therefore, we will not include the pure sFBM or sFLM models in the
+  remainder of our analysis.
 
@@
   \end{subfigure}
-  \caption{(a) Simulated urea trajectories generated by each of the four variations of 
-  the one mode AD model display qualitatively similar hopping and trapping behavior to
-  that shown in Figure~\ref{fig:solute_trajectories}. Dwell times are exaggerated in 
-  the sFBM and sFLM models because the power law dwell time distributions are not 
-  truncated and have infinite variance. In (b) and (c) we compare additional 
-  trajectories simulated with the sFBMcut and sFLMcut models (blue) to
-  MD solute trajectories (black). Trajectories are vertically offset for visual clarity.
+  \caption{(a) Simulated urea trajectories generated by each of the four
+	  variations of the one mode AD model display qualitatively similar
+	  hopping and trapping behavior to that shown in
+	  Figure~\ref{fig:solute_trajectories}. Dwell times are exaggerated in
+	  the sFBM and sFLM models because the power law dwell time
+	  distributions are not truncated and have infinite variance. In (b)
+	  and (c) we compare additional trajectories simulated with the sFBMcut
+	  and sFLMcut models (blue) to MD solute trajectories (black).
+	  Trajectories are vertically offset for visual clarity.
   }\label{fig:ad_eyetest}
@@
 
-%  We evaluated the predictive capabilities of the AD modeling approach by training
-%  the model parameters on the first half of the equilibrated MD trajectory data and
-%  then comparing the MSD calculated from AD model realizations to the MSD calculated
-%  from the second half of the equilibrated MD trajectory data. This metric is
-%  only meaningful if the ensemble of solute trajectories is stationary.
-
-  We observe that in some cases, solute trajectories extracted from our MD simulations
-  display non-stationary behavior. We defined the perceived equilibration time point for
-  each solute based on the time at which the number of solutes inside the pores and tails
-  stabilized (Figure~\ref{S-fig:equilibration}).  
-  With this definition, we observe evidence of non-stationary solute behavior after 
-  the perceived equilibration point, on the $\mu$s timescale. In Table~\ref{table:stationarity},
-  we compare the MSD of the solutes calculated using trajectory data from the first and
-  second halves of the ``equilibrated" simulation time. Ethylene glycol and methanol show
-  considerable differences between the MSDs of the two halves. Urea and acetic acid appear
-  to demonstrate satisfactory stationarity. The shapes of their MSD curves are also very 
-  similar (see Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).
+  We observe that in some cases, solute trajectories extracted from our MD
+  simulations display non-stationary behavior. We defined the perceived
+  equilibration time point for each solute based on the time at which the
+  number of solutes inside the pores and tails stabilized
+  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
+  evidence of non-stationary solute behavior after the perceived equilibration
+  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
+  the MSD of the solutes calculated using trajectory data from the first and
+  second halves of the ``equilibrated" simulation time. Ethylene glycol and
+  methanol show considerable differences between the MSDs of the two halves.
+  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
+  shapes of their MSD curves are also very similar (see
+  Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).
 
@@
   \end{tabular}
-  \caption{In order to be considered stationary, the MSD of the ensemble of solute 
-  trajectories should be the same independent of the portion of equilibrated 
-  trajectory that is analyzed. The MSD values in this table are averages taken 
-  after a 500 ns time lag, calculated independently from the first and second 
-  halves of the equilibrated solute trajectories. Urea and acetic acid both 
-  appear to satisfy the stationarity criteria, while ethylene glycol and methanol
-  show significantly smaller MSDs when calculated from the second half of the 
-  equilibrated trajectories.}\label{table:stationarity}
+  \caption{In order to be considered stationary, the MSD of the ensemble of
+	  solute trajectories should be the same independent of the portion of
+	  equilibrated trajectory that is analyzed. The MSD values in this
+	  table are averages taken after a 500 ns time lag, calculated
+	  independently from the first and second halves of the equilibrated
+	  solute trajectories. Urea and acetic acid both appear to satisfy the
+	  stationarity criteria, while ethylene glycol and methanol show
+	  significantly smaller MSDs when calculated from the second half of
+	  the equilibrated trajectories.}\label{table:stationarity}
   \end{table}
@@
   Given stationary data, the AD approach is capable of predicting solute MSDs
-  measured from MD simulations within or near statistical uncertainty.
-  In Figure~\ref{S-fig:train_test} of the Supplemental Material, we parameterized 
-  the AD models using the first half of the stationary solute equilibrated trajectories 
-  and then compared the model predictions to the MD MSD of the second of half 
-  of the stationary trajectories. In most cases, the model predictions fall within
-  the 1$\sigma$ confidence intervals of the MD MSD.
-
-  This brief analysis suggests that we may be operating on the border of the minimum 
-  amount of data required to accurately parameterize the AD model. Working with 
-  only half of the data we collected ($\sim$ 2 $\mu$s post-equilibration) may not
-  always be sufficient for extracting reliable parameter estimates. Therefore, for 
-  the remainder of this work, we will employ parameters fit to the entire
-  equilibrated portion of the solute trajectories. Even doubling the data might 
-  not be good enough for molecules with statistical non-stationarity, meaning the
-  predictive and interpretive power of the time series modeling applied to these 
-  trajectories will be lower.
+  measured from MD simulations within or near statistical uncertainty. In
+  Figure~\ref{S-fig:train_test} of the Supplemental Material, we parameterized
+  the AD models using the first half of the stationary solute equilibrated
+  trajectories and then compared the model predictions to the MD MSD of the
+  second half of the stationary trajectories. In most cases, the model
+  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.
+
+  This brief analysis suggests that we may be operating on the border of the
+  minimum amount of data required to accurately parameterize AD approach
+  models. Working with only half of the data we collected ($\sim$ 2 $\mu$s
+  post-equilibration) may not always be sufficient for extracting reliable
+  parameter estimates. Therefore, for the remainder of this work, we will
+  employ parameters fit to the entire equilibrated portion of the solute
+  trajectories. Even doubling the data might not be good enough for molecules
+  with statistical non-stationarity, meaning the predictive and interpretive
+  power of the time series modeling applied to these trajectories will be
+  lower.
 
@@
 
-  %MRS8: does it make sense to say ``the AD model'', when there are several variants? 
-  %would it be better to say ``the AD approach''?
-  We obtain reasonable predictions of the MD simulated MSDs when we parameterize AD 
-  models with all available data after the perceived equilibration time.  
-  The MSD curves generated from the 1 and 2 mode models are overlayed with the MD 
-  simulated MSDs for comparison in Figure~\ref{fig:anomalous_msds}. The associated 
-  parameters for the 1 and 2 mode models are presented in Figures~\ref{fig:1mode_parameters}
+  We obtain reasonable predictions of the MD simulated MSDs when we
+  parameterize AD models with all available data after the perceived
+  equilibration time. The MSD curves generated from the 1 and 2 mode models
+  are overlayed with the MD simulated MSDs for comparison in
+  Figure~\ref{fig:anomalous_msds}. The associated parameters for the 1 and 2
+  mode models are presented in Figures~\ref{fig:1mode_parameters}
   and~\ref{fig:2mode_parameters}.
@@
   \end{subfigure}
-  \caption{In most cases, MSDs generated from realizations of both the one and two
-  mode AD models lie within or near the 1$\sigma$ confidence intervals of MD-generated 
-  data. Drawing hops from a truncated L\'evy stable distribution (sFLMcut) yields
-  MSDs similar to  when hops are drawn from Gaussian distributions (sFBMcut). 
-  In most cases, the one mode simulated MSDs under-predicted the mean at long timescales
-  partially because they show pronounced curvature which the MD MSDs lack. The two mode
-  predictions show less curvature than the one mode MSDs because the hop correlation 
-  structure is broken every time a transition between tails occurs.
+  \caption{In most cases, MSDs generated from realizations of both the one and
+	  two mode AD models lie within or near the 1$\sigma$ confidence
+	  intervals of MD-generated data. Drawing hops from a truncated L\'evy
+	  stable distribution (sFLMcut) yields MSDs similar to when hops are
+	  drawn from Gaussian distributions (sFBMcut). In most cases, the one
+	  mode simulated MSDs under-predicted the mean at long timescales
+	  partially because they show pronounced curvature which the MD MSDs
+	  lack. The two mode predictions show less curvature than the one mode
+	  MSDs because the hop correlation structure is broken every time a
+	  transition between tails occurs.
   }\label{fig:anomalous_msds}
@@
   \end{subfigure}
-  \caption{The parameters of the one mode model reveal differences in dynamics between
-  solutes. (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, and L\'evy stable, 
-  $L(\sigma, \alpha_h)$, distributions to describe solute hop lengths. We assume the 
-  mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta = 0$)
-  in the L\'evy stable distributions. High values of $\sigma$ and lower values of $\alpha_h$
-  result in larger hops. (b) We parameterized a pure power law, $P(\alpha)$, and a 
-  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe solute dwell
-  times. Lower values of $\alpha$ lead to heavier power law tails and higher values of 
-  $\lambda$ truncate the distribution at lower dwell times. (c) Finally, we parameterized the
-  hop autocorrelation function, $\gamma(H)$, to describe the degree of correlation between
-  hops. Higher values of $H$ display closer to Brownian behavior.}\label{fig:1mode_parameters}
+  \caption{The parameters of the one mode model reveal differences in dynamics
+	  between solutes. (a) We parameterized Gaussian,
+	  $\mathcal{N}(\sigma)$, and L\'evy stable, $L(\sigma, \alpha_h)$,
+	  distributions to describe solute hop lengths. We assume the mean
+	  ($\mu$) to be zero for these distributions and there to be no
+	  skewness ($\beta = 0$) in the L\'evy stable distributions. High
+	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
+	  hops. (b) We parameterized a pure power law, $P(\alpha)$, and a
+	  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe
+	  solute dwell times. Lower values of $\alpha$ lead to heavier power
+	  law tails and higher values of $\lambda$ truncate the distribution at
+	  lower dwell times. (c) Finally, we parameterized the hop
+	  autocorrelation function, $\gamma(H)$, to describe the degree of
+	  correlation between hops. Higher values of $H$ display closer to
+	  Brownian behavior.}\label{fig:1mode_parameters}
   \end{figure}
@@
   \end{subfigure}
-  \caption{
-  The two mode model parameterizes solute behavior in the pore and tails separately.
-  We consider solutes to be within the pore region if they are 0.75 nm from a given pore
-  center, otherwise they are in the tails. (a) Generally, movement is much more restricted
-  in the tail region, parameterized by lower $\sigma$ values (smaller hops) for the 
-  Gaussian and L\'evy stable distributions. Values of $\alpha_h$ are significantly lower for urea and acetic acid meaning 
-  there is a larger probability that they will take large hops. (b) Dwell times are longer in 
-  the tails. Lower values of $\alpha$ correspond to power laws with heavier tails and 
-  thus higher probabilities of long dwell times. There is no easily discernible trend in
-  $\lambda$ of the truncated power law distribution. Note that we used the same Hurst parameter
-  for both modes (shown in Figure~\ref{fig:hurst_barchart}) due to a low number of 
-  sufficiently long sequences of hops in each mode. (c) Solutes spend various amounts of 
-  time in the tail and pore region dependent on their size, shape and chemical functionality.
-  Methanol's small size favors occupation of the much larger accessible volume in the tails. 
-  Urea and acetic acid are fairly stable in both regions since they are small and hydrophilic.
-  Ethylene glycol has a slight preference for the pores likely because it is a larger molecule
-  with two hydrophilic hydroxyl groups.
+  \caption{The two mode model parameterizes solute behavior in the pore and tails
+	  separately. We consider solutes to be within the pore region if they
+	  are 0.75 nm from a given pore center, otherwise they are in the
+	  tails. (a) Generally, movement is much more restricted in the tail
+	  region, parameterized by lower $\sigma$ values (smaller hops) for the
+	  Gaussian and L\'evy stable distributions. Values of $\alpha_h$ are
+	  significantly lower for urea and acetic acid meaning there is a
+	  larger probability that they will take large hops. (b) Dwell times
+	  are longer in the tails. Lower values of $\alpha$ correspond to power
+	  laws with heavier tails and thus higher probabilities of long dwell
+	  times. There is no easily discernible trend in $\lambda$ of the
+	  truncated power law distribution. Note that we used the same Hurst
+	  parameter for both modes (shown in Figure~\ref{fig:hurst_barchart})
+	  due to a low number of sufficiently long sequences of hops in each
+	  mode. (c) Solutes spend various amounts of time in the tail and pore
+	  region dependent on their size, shape and chemical functionality.
+	  Methanol's small size favors occupation of the much larger accessible
+	  volume in the tails. Urea and acetic acid are fairly stable in both
+	  regions since they are small and hydrophilic. Ethylene glycol has a
+	  slight preference for the pores likely because it is a larger
+	  molecule with two hydrophilic hydroxyl groups.
   }\label{fig:2mode_parameters}
@@
 
-  The one and two mode AD models do a fairly good job of predicting the magnitude of 
-  the MD MSD curves examined up to a 1000 ns time lag.
-  % when we use truncated power
-  %laws to describe the dwell time distributions.
-  %MRS8: maybe be a bit more explicit about which choices described above are used here. i.e. did you actually use a Gaussian  distribution because Levy was so close?
-  %BJC8: I thought that sFBMcut and sFLMcut implied which distributions I used. It's in Table I
-  In most cases, the sFBMcut and sFLMcut models give very similar results, most 
-  likely because their $\alpha_h$ parameter values are relatively close to 2, meaning
-  the hop length distributions are nearly Gaussian even when fit to a more general 
+  The one and two mode AD models do a fairly good job of predicting the
+  magnitude of the MD MSD curves examined up to a 1000 ns time lag. In most
+  cases, both the Brownian (sFBMcut) and L\'evy (sFLMcut) versions of both the
+  one and two mode AD models give very similar results, most likely because
+  their $\alpha_h$ parameter values are relatively close to 2, meaning the hop
+  length distributions are nearly Gaussian even when fit to a more general
   L\'evy distribution.
@@
   The deviation between the one mode MSD predictions and MD are primarily due
-  to differences in their curvature at long time lags. The shape and magnitude of 
-  the predicted curves appears accurate relative to MD at short time lags.  
-  However, the modeled trajectories undershoot the mean MD MSD as the time lag increases. As 
-  discussed in the previous section, long time positional anti-correlation, on
-  the order of hundreds of ns, may not exist in the MD system. 
-  %MRS8: maybe there should be something here like ``as the system moves to independent parts of the pore, but this correlation does exist in the time series modeling''.
-  Eventual loss of correlation would result in a shift from sub-linear to linear 
-  MSD behavior, as observed in the MD trajectories. Acetic acid exemplifies this point.
-  At first glance, acetic acid's predicted MSD appears to match the curvature of MD 
-  quite well, but closer examination reveals that the MD MSD curve actually shifts
-  from a sub-linear to a linear regime around 500 ns.
-
-  The two mode models display curvature more consistent with MD but for non-physical
-  reasons. Every time a switch between the pores and tails occurs, the width of the
-  distribution used to model hops changes. We are unaware of an appropriate technique which can 
-  correlate hops that come from different hop distributions, therefore every 
-  time a mode switch occurs, the correlation structure is broken. Solutes that
-  switch between modes the least show predicted MSDs with the greatest curvature. 
-  Due to the much larger accessible volume that a smaller molecule has, methanol 
-  spends $>90\%$ of its time in the hydrophobic tails (see Figure~\ref{fig:AD_mode_occupation}),
-  so mode transitions are relatively rare and the predicted MSDs have significant 
-  curvature. This artificially solves the problem of long timescale correlation, 
-  however we do not recommend this as it has no physical basis.
-
-  The model parameters for the one and two mode models tell stories about each solute's
-  behavior that help explain the difference between the MSDs of different solutes. 
-  Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
-  hop length magnitudes by increasing the hop length distribution's width and tail 
-  density respectively. Higher values of $\alpha$ indicate a lower probability of 
-  long dwell times. Higher values of $\lambda$ truncate the power law distribution 
-  earlier preventing extremely long dwell times. Values of $H$ closer to the Brownian
-  limit of 0.5 indicate a lower degree of negative correlation between hops. All 
-  of these changes in physical behavior contribute to an overall increase in the 
-  predicted MSD.
-
-  Turning first to the parameters of the one mode model, we can begin to break down the
-  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
-  relatively similar which is consistent with their similar MD MSDs. Relative to 
-  ethylene glycol, methanol tends to stay trapped for less time and takes larger hops
-  but the most substantial difference is with respect to their Hurst parameters.  
-  Methanol has the lowest $H$ of all the solutes studied because it spends the majority
-  of its time outside the pore region where collisions with tails are frequent.
+  to differences in their curvature at long time lags. The shape and magnitude
+  of the predicted curves appears accurate relative to MD at short time lags.
+  However, the modeled trajectories undershoot the mean MD MSD as the time lag
+  increases. As discussed in the previous section, long time positional
+  anti-correlation, on the order of hundreds of ns, may not exist in the MD
+  system. Eventual loss of correlation would result in a shift from sub-linear
+  to linear MSD behavior, as observed in the MD trajectories. Acetic acid
+  exemplifies this point. At first glance, acetic acid's predicted MSD appears
+  to match the curvature of MD quite well, but closer examination reveals that
+  the MD MSD curve actually shifts from a sub-linear to a linear regime around
+  500 ns.
+
+  The two mode models display curvature more consistent with MD but for
+  non-physical reasons. Every time a switch between the pores and tails occurs,
+  the width of the distribution used to model hops changes. We are unaware of
+  an appropriate technique which can correlate hops that come from different
+  hop distributions, therefore every time a mode switch occurs, the correlation
+  structure is broken. Solutes that switch between modes the least show
+  predicted MSDs with the greatest curvature. Due to the much larger
+  accessible volume that a smaller molecule has, methanol spends $>90\%$ of its
+  time in the hydrophobic tails (see Figure~\ref{fig:AD_mode_occupation}), so
+  mode transitions are relatively rare and the predicted MSDs have significant
+  curvature. This artificially solves the problem of long timescale
+  correlation, however we do not recommend this as it has no physical basis.
+
+  The model parameters for the one and two mode models tell stories about each
+  solute's behavior that help explain the difference between the MSDs of
+  different solutes. Higher values of $\sigma$ and lower values of $\alpha_h$
+  indicate larger average hop length magnitudes by increasing the hop length
+  distribution's width and tail density respectively. Higher values of $\alpha$
+  indicate a lower probability of long dwell times. Higher values of $\lambda$
+  truncate the power law distribution earlier preventing extremely long dwell
+  times. Values of $H$ closer to the Brownian limit of 0.5 indicate a lower
+  degree of negative correlation between hops. All of these changes in physical
+  behavior contribute to an overall increase in the predicted MSD.
+
+  Turning first to the parameters of the one mode model, we can begin to break
+  down the trends in solute MSDs. The parameters belonging to ethylene glycol
+  and methanol are relatively similar which is consistent with their similar MD
+  MSDs. Relative to ethylene glycol, methanol tends to stay trapped for less
+  time and takes larger hops but the most substantial difference is with
+  respect to their Hurst parameters. Methanol has the lowest $H$ of all the
+  solutes studied because it spends the majority of its time outside the pore
+  region where collisions with tails are frequent.
 % BJC: made more to the point
@@
 %  with tails are frequent. 
-  Urea has the third highest MSD which is primarily a consequence of more frequent and
-  longer dwell times (lower $\alpha$ and $\lambda$). Urea's hop lengths ($\sigma$) and
-  correlation ($H$) are comparable to ethylene glycol and methanol. Acetic acid has the
-  smallest MSD among the solutes studied due to longer periods of entrapment and shorter
-  hops. Its trapping behavior is parameterized by an $\alpha$ value significantly lower
-  than other solutes, but an intermediate $\lambda$ value, suggesting it experiences 
-  many medium-length periods of entrapment. Its hops are smaller but are slightly 
-  compensated by a heavier tailed distribution (lower $\alpha_h$) than the other solutes.
-
-  We can use the two mode model to gain an even deeper understanding of solute behavior
-  in the pore versus in the tails. It is clear that solutes are significantly slowed 
-  while they are in the tail region where long dwell times are more probable
-  (smaller $\alpha$) and hops are smaller (smaller $\sigma$). Each solute spends 
-  a different amount of time in the tails (see Figure~\ref{fig:AD_mode_occupation}). 
-  Urea and acetic acid spend slightly more than half of their time in the tails 
-  (56\% and 62\% of their time respectively) while ethylene glycol spends about 
-  44\% of its time in the tails. Urea and acetic acid's compact and flat structure 
-  allows it to more easily partition into the tails while ethylene glycol prefers
-  the pore region due to its two hydrophilic hydroxyl groups. In contrast, methanol 
-  spends 91\% of its time in the tails, likely due to its small size.  
-  The value of $\alpha_h$ for urea and acetic acid in the tails is 1.50, meaning its hop distribution
-  is heavy tailed relative to ethylene glycol and methanol, whose $\alpha_h$ values are
-  1.90 and 1.85 respectively, which is more consistent with a Gaussian distribution ($\alpha$=2).
-  Acetic acid and urea are structurally similar molecules, both planar with two heavy atoms attached to a 
-  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
-  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
-  to make larger jumps to escape traps.
-
-  Overall, the AD approach does a reasonable job of predicting solute MSDs and its 
-  parameters can help us further understand solute dynamics. Hops appear to be well
-  modeled as anti-correlated draws from either Gaussian or L\'evy stable distributions. 
-  The data strongly suggests that one must truncate the power law dwell time 
-  distributions in order to obtain accurate MSD estimates. Trajectories generated 
-  by pure power laws are qualitatively non-physical. We can further understand
-  solute dynamics by adding radially dependent parameter distributions as in the 
-  2 mode model. A significant amount of solute trajectory data is necessary 
-  in order to achieve good parameter estimates. 
-  %MRS8: seems kind of obvious.
+  Urea has the third highest MSD which is primarily a consequence of more
+  frequent and longer dwell times (lower $\alpha$ and $\lambda$). Urea's hop
+  lengths ($\sigma$) and correlation ($H$) are comparable to ethylene glycol
+  and methanol. Acetic acid has the smallest MSD among the solutes studied due
+  to longer periods of entrapment and shorter hops. Its trapping behavior is
+  parameterized by an $\alpha$ value significantly lower than other solutes,
+  but an intermediate $\lambda$ value, suggesting it experiences many
+  medium-length periods of entrapment. Its hops are smaller but are slightly
+  compensated by a heavier tailed distribution (lower $\alpha_h$) than the
+  other solutes.
+
+  We can use the two mode model to gain an even deeper understanding of solute
+  behavior in the pore versus in the tails. It is clear that solutes are
+  significantly slowed while they are in the tail region where long dwell times
+  are more probable (smaller $\alpha$) and hops are smaller (smaller $\sigma$).
+  Each solute spends a different amount of time in the tails (see
+  Figure~\ref{fig:AD_mode_occupation}). Urea and acetic acid spend slightly
+  more than half of their time in the tails (56\% and 62\% of their time
+  respectively) while ethylene glycol spends about 44\% of its time in the
+  tails. Urea and acetic acid's compact and flat structure allows it to more
+  easily partition into the tails while ethylene glycol prefers the pore region
+  due to its two hydrophilic hydroxyl groups. In contrast, methanol spends 91\%
+  of its time in the tails, likely due to its small size. The value of
+  $\alpha_h$ for urea and acetic acid in the tails is 1.50, meaning its hop
+  distribution is heavy tailed relative to ethylene glycol and methanol, whose
+  $\alpha_h$ values are 1.90 and 1.85 respectively, which is more consistent
+  with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
+  structurally similar molecules, both planar with two heavy atoms attached to
+  a carbonyl group. Their small size and rigid shape may allow them to
+  occasionally slip through gaps in the tails. Meanwhile, methanol is small
+  enough that it does not need to make larger jumps to escape traps.
+
+  Overall, the AD approach does a reasonable job of predicting solute MSDs and
+  its parameters can help us further understand solute dynamics. Hops appear to
+  be well modeled as anti-correlated draws from either Gaussian or L\'evy
+  stable distributions. The data strongly suggests that one must truncate the
+  power law dwell time distributions in order to obtain accurate MSD estimates.
+  Trajectories generated by pure power laws are qualitatively non-physical. We
+  can further understand solute dynamics by adding radially dependent parameter
+  distributions as in the 2 mode model. A significant amount of solute
+  trajectory data is necessary in order to achieve good parameter estimates. 
 %  The exact amount of data required is dependent on the solute studied.
@@
 
-  %BJC5: could remove this transitional paragraph
-  %MRS8: helps flow, so probably OK.
-  %MRS8: Model vs. approach. Though the 2 state does involve some mechanistic detail (partitioning) so the below isn't quite true.
   The AD model is useful if one does not know exact transport mechanisms 
@@
 
-  %BJC6: added subsection title
   \subsubsection{Solute state preferences}\label{section:state_preferences}
 
-  Solute size and chemical functionality influence which states are visited most frequently.
-  In Figure~\ref{fig:state_probabilities}, we plotted the probabilities of occupying
-  a given state at any time. Solutes tend to favor the same types of interactions 
-  independent of which region they are in. 
-  %BJC8: added following sentence  
-  We can relate these interactions to solute chemical functionality and use that intuition
-  to hypothesize new designs for LLC monomers which control the transport rate of specific
-  solutes.
+  Solute size and chemical functionality influence which states are visited
+  most frequently.  In Figure~\ref{fig:state_probabilities}, we plotted the
+  probabilities of occupying a given state at any time. Solutes tend to favor
+  the same types of interactions independent of which region they are in.  We
+  can relate these interactions to solute chemical functionality and use that
+  intuition to hypothesize new designs for LLC monomers which control the
+  transport rate of specific solutes.
 
@@
   \caption{Solutes spend varying amounts of time under the influence of each
-  trapping mechanism. To aid the reader, we labeled each state with an abbreviation which
-  identifies the combination of conditions to which each solute is subject in each state:
-  t - tails, p - pores, h - hydrogen bonded, a - associated with sodium. Solutes tend to 
-  favor the same types of interactions (e.g. hydrogen bonding and/or associating with sodium
-  ions) independent of whether they are in the pores or the tails.}\label{fig:state_probabilities}
+	  trapping mechanism. To aid the reader, we labeled each state with an
+	  abbreviation which identifies the combination of conditions to which
+	  each solute is subject in each state: t - tails, p - pores, h -
+	  hydrogen bonded, a - associated with sodium. Solutes tend to favor
+	  the same types of interactions (e.g. hydrogen bonding and/or
+	  associating with sodium ions) independent of whether they are in the
+	  pores or the tails.}\label{fig:state_probabilities}
   \end{figure}
 
-  %MRS8: in section below, it would be useful to add a sentence that answers the ``so, what'' after the structural
-  %detail for each molecule - just adds reader interest.
-  %BJC8: I'm interpreting this as, "how does this information relate to design"
-  Urea spends the largest fraction of its time trapped via association with sodium ions.
-  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
-  total time while in the pores (state 7). Note that sodium does not drift significantly 
-  into the tails but sits close to the pore/tail region boundary. The electron-dense 
-  and unshielded oxygen atom of urea's carbonyl group is prone to associate with 
-  positively charged sodium ions. The nitrogen atoms of urea are only weak hydrogen bond
-  donors. 
-  %BJC8: something like this I think.   
-  Therefore the transport rate of urea may be enhanced the most by removing or changing 
-  the counter-ion identity.
-  %MRS8: above seems incomplete - are weak h-bond donors so what?
+  Urea spends the largest fraction of its time trapped via association with
+  sodium ions. It does so 31\% of the total time while in the tails (state 3)
+  and 21\% of the total time while in the pores (state 7). Note that sodium
+  does not drift significantly into the tails but sits close to the pore/tail
+  region boundary. The electron-dense and unshielded oxygen atom of urea's
+  carbonyl group is prone to associate with positively charged sodium ions. The
+  nitrogen atoms of urea are only weak hydrogen bond donors. Therefore, the
+  transport rate of urea is likely to be most significantly modified by
+  removing or changing the identity of the counter-ion.
 
@@
   bonded state. It does so 24\% of the total time while in the tails (state 2)
-  and 32\% of the total time while in the pores (state 6). The two hydroxyl groups 
-  of ethylene glycol readily donate their hydrogen atoms to the carboxylate
-  head groups and the ether linkages between the head groups and monomer tails.
-  %BJC8: added following sentence
-  The transport rate of ethylene glycol might be increased by removing hydrogen 
-  bond accepting groups from the LLC monomers, especially those which stabilize
-  the solute in the tails (i.e. the ether linkages).
-
-  Methanol spends most of its time unbound in the tail region (state 1) and spends a 
-  significant portion of time hydrogen bonded while in the tail region.
-  Tail region hydrogen bonds are donated from methanol to the ether linkages between
-  the monomer head groups and tails. 
-  %BJC8: added  
-  If one desires an increased methanol transport 
-  rate, the LLC system may benefit most by preventing its partition into the monomer
-  tails. This might be achieved by adding cross-linkable groups near the monomer
-  head groups.
-
-  Finally, acetic acid spends the majority of its time hydrogen bonding both in and out
-  of the pore (states 2 and 6). Although it has an unshielded carbonyl group in its
-  structure, association with sodium ions in this environment is apparently a much 
-  weaker interaction than hydrogen bonding. 
-  %BJC8:added  
-  As with ethylene glycol, one might increase
-  the transport rate of acetic acid by removing hydrogen bond accepting constituents
-  of the LLC monomer. With this modification, we hypothesize that acetic acid would 
-  show similar transport rates to urea given their structural similarity.
-
-  % BJC6: cut down the following paragraph by eliminating things that are in the methods. 
-%  There are not enough 
-%  consecutive observations of each type of transition with which to study their 
-%  individual correlation structures so we grouped all transition distributions
-%  into a single distribution and measured the correlation of the series of all 
-%  transitions. 
-%  %MRS6: how much of this is described earlier in methods?
-%  We lose information about individual types of transitions, however, 
-%  we believe this is unavoidable without at least an order of magnitude of additional data.
-%  In theory, one could parameterize separate transition distributions for those
-%  which occur in the tails versus in the pores, however this would lead to a broken 
-%  correlation structure similar to that seen in the 2 mode AD model.
+  and 32\% of the total time while in the pores (state 6). The two hydroxyl
+  groups of ethylene glycol readily donate their hydrogen atoms to the
+  carboxylate head groups and the ether linkages between the head groups and
+  monomer tails. The transport rate of ethylene glycol might be modified by
+  removing hydrogen bond accepting groups from the LLC monomers, especially
+  those which stabilize the solute in the tails (i.e. the ether linkages).
+
+  Methanol spends most of its time unbound in the tail region (state 1) and
+  spends a significant portion of time hydrogen bonded while in the tail
+  region. Tail region hydrogen bonds are donated from methanol to the ether
+  linkages between the monomer head groups and tails. One might modify the
+  rate of methanol transport by controlling its partition into the monomer
+  tails. This might be achieved by adding cross-linkable groups near the
+  monomer head groups.
+
+  Finally, acetic acid spends the majority of its time hydrogen bonding both in
+  and out of the pore (states 2 and 6). Although it has an unshielded carbonyl
+  group in its structure, association with sodium ions in this environment is
+  apparently a much weaker interaction than hydrogen bonding.  As with ethylene
+  glycol, one might modify the transport rate of acetic acid by removing
+  hydrogen bond accepting constituents of the LLC monomer. With this
+  modification, we hypothesize that acetic acid might show similar transport
+  rates to urea given their structural similarity.
 
@@
   versus in the pores, however this would lead to a broken correlation structure 
-  similar to that seen in the two mode AD model.
+  similar to that seen in the two mode AD models.
 
   We observe correlated emissions drawn from L\'evy stable distributions. The
-  deviation of the emission distributions from Gaussian behavior is far more pronounced
-  than that seen in the hop length distributions of the previous section, and therefore we 
-  did not consider the Gaussian case (see Figure~\ref{fig:gaussian_levy_comparison}).
-  The correlation structure between hops is consistent with that of FLM (Figure~\ref{fig:msddm_acf}).
-  The parameters of the L\'evy stable distributions along with their Hurst parameters 
-  are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated in the Supporting
-  Information, Table~\ref{S-table:msddm_params}).
+  deviation of the emission distributions from Gaussian behavior is far more
+  pronounced than that seen in the hop length distributions of the previous
+  section, therefore we did not consider the Gaussian case (see
+  Figure~\ref{fig:gaussian_levy_comparison}). The correlation structure
+  between hops is consistent with that of FLM (Figure~\ref{fig:msddm_acf}).
+  The parameters of the L\'evy stable distributions along with their Hurst
+  parameters are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated
+  in the Supplemental Material, Table~\ref{S-table:msddm_params}).
 
@@
   \caption{(a) The emission distributions of hop lengths are non-Gaussian and
-  heavy-tailed. Shown here is the emission distribution for transitions between
-  states. The maximum likelihood Gaussian fit severely underestimates the empirical
-  density of hops near and far from zero while overestimating the density of hops
-  at intermediate values. (b) Jumps drawn from the transition distribution are 
-  negatively correlated to each other. The normalized version of 
-  Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
-  an appropriate way to model jumps.} \label{fig:msddm_emissions}
+	  heavy-tailed. Shown here is the emission distribution for transitions
+	  between states. The maximum likelihood Gaussian fit severely
+	  underestimates the empirical density of hops near and far from zero
+	  while overestimating the density of hops at intermediate values. (b)
+	  Jumps drawn from the transition distribution are negatively
+	  correlated to each other. The normalized version of
+	  Equation~\ref{eqn:flm_autocovariance} fits well to the data
+	  suggesting FLM is an appropriate way to model jumps.}
+	  \label{fig:msddm_emissions}
   \end{figure}
@@
   \end{subfigure}
-  \caption{The parameters of the MSDDM are strong functions of trapping mechanisms.
-  We observe different parameters but with similar trends between the tail and pore
-  region. The states are defined in Table~\ref{table:states}. See Figure~\ref{fig:state_probabilities}
-  for a description of the abbreviation under each state number. The legend in (a) applies to all subplots. (a) Motion is
-  highly anti-correlated in trapped states. As the number of simultaneously influencing
-  trapping mechanisms increases, the Hurst parameter, $H$, decreases. $H$ is
-  highest during transitions between states (state T). (b) As more trapping mechanisms
-  simultaneously influence solutes, the width of the hop length distribution ($\sigma$) decreases.
-  The largest hops occur when solutes are unbound in the pores. (c) The weight of the 
-  hop length distribution's tails, parameterized by $\alpha_h$, increases as more trapping
-  mechanisms influence solutes simultaneously. The transition hop distributions have
-  among the heaviest tails.}\label{fig:msddm_parameters}
+  \caption{The parameters of the MSDDM are strong functions of trapping
+	  mechanisms. We observe different parameters but with similar trends
+	  between the tail and pore region. The states are defined in
+	  Table~\ref{table:states}. See Figure~\ref{fig:state_probabilities}
+	  for a description of the abbreviation under each state number. The
+	  legend in (a) applies to all subplots. (a) Motion is highly
+	  anti-correlated in trapped states. As the number of simultaneously
+	  influencing trapping mechanisms increases, the Hurst parameter, $H$,
+	  decreases. $H$ is highest during transitions between states (state
+	  T). (b) As more trapping mechanisms simultaneously influence solutes,
+	  the width of the hop length distribution ($\sigma$) decreases.  The
+	  largest hops occur when solutes are unbound in the pores. (c) The
+	  weight of the hop length distribution's tails, parameterized by
+	  $\alpha_h$, increases as more trapping mechanisms influence solutes
+	  simultaneously. The transitional hop distributions have among the
+	  heaviest tails.}\label{fig:msddm_parameters}
   \end{figure}
@@
   Most of a solute's MSD is a consequence of transitions between the 8 states
-  in Table~\ref{table:states}. Perfectly anti-correlated motion ($H$=0) results in
-  no contribution to the solute's MSD. Motion while trapped in a state is highly 
-  anti-correlated as indicated by their consistently low Hurst parameters.
-  There is a weak negative trend in the Hurst parameter values as the number
-  of simultaneously influencing trapping mechanisms increases (Figure~\ref{fig:H_v_state}). 
-  % BJC7: Following is unsupported by data and therefore just a hypothesis
-%  Surprisingly, state 5 $H$ values are low despite the solutes being subject to no
-%  trapping mechanisms. Highly anti-correlated behavior in the pores in the absence of
-%  any trapping mechanism is likely caused by collisions with monomer head groups 
-%  within the pore region. 
-  The Hurst parameters for transitional (T) emissions are up to 18 times higher than
-  emissions from trapped states. The value of $\alpha_h$ for 
-  transition emissions is also relatively low giving higher probabilities to larger hops.
-
-  As solutes are influenced by more trapping interactions simultaneously (e.g.~hydrogen
-  bonding \textit{and} association with sodium versus just hydrogen bonding), the 
-  width of the hop length distribution, $\sigma$, decreases while its L\'evy index,
-  $\alpha_h$, increases. Treating states in the tail and pore regions independently, 
-  $\sigma$ is largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding
-  or associating with sodium (states 1 and 5). Solutes are free to move and take 
-  occasionally large hops. The smallest $\sigma$ and highest $\alpha_h$ values are
-  measured when solutes are hydrogen bonding and associating with sodium at the
-  same time (states 4 and 8). Motion is restricted by 
-  %MRS8: unclear what multiple tethers means. 
-  multiple tethers which 
-  maintains a relatively narrow distribution of hop lengths.
-
-%  The trapping mechanisms affect each solute to varying degrees. The probabilities
-%  of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
-%  Urea and acetic acid spend slightly more than half their time in the tails (56\% and 62\% 
-%  of their time respectively) while ethylene glycol spends about 44\% of its time in the tails.
-%  Urea and acetic acid's compact and flat structure allows it to more easily 
-%  partition into the tails while ethylene glycol prefers the pore region due to 
-%  its two hydrophilic hydroxyl groups. Meanwhile methanol spends 91 \% of its 
-%  time in the tails likely due to its small size.
+  in Table~\ref{table:states}. Perfectly anti-correlated motion ($H$=0) results
+  in no contribution to the solute's MSD. Motion while trapped in a state is
+  highly anti-correlated as indicated by their consistently low Hurst
+  parameters. There is a weak negative trend in the Hurst parameter values as
+  the number of simultaneously influencing trapping mechanisms increases
+  (Figure~\ref{fig:H_v_state}).  The Hurst parameters for transitional (T)
+  emissions are up to 18 times higher than emissions from trapped states. The
+  value of $\alpha_h$ for transition emissions is also relatively low giving
+  higher probabilities to larger hops.
+
+  As solutes are influenced by more trapping interactions simultaneously
+  (e.g.~hydrogen bonding \textit{and} association with sodium versus just
+  hydrogen bonding), the width of the hop length distribution, $\sigma$,
+  decreases while its L\'evy index, $\alpha_h$, increases. Treating states in
+  the tail and pore regions independently, $\sigma$ is largest and $\alpha_h$
+  is smallest when solutes are not hydrogen bonding or associating with sodium
+  (states 1 and 5). Solutes are free to move and take occasionally large hops.
+  The smallest $\sigma$ and highest $\alpha_h$ values are measured when solutes
+  are hydrogen bonding and associating with sodium at the same time (states 4
+  and 8). Motion is restricted by multiple stabilizing forces which maintains a
+  relatively narrow distribution of hop lengths.
 
@@
 
-% reordered this section to make the logic more clear
-
-  %Despite qualitative differences in trajectory realizations, 
   The dynamics of urea, ethylene glycol and, to a lesser extent, methanol appear
@@
   the magnitude of the MD MSDs within their 1$\sigma$ confidence intervals.
-  %One 
-  %could argue that the curves of ethylene glycol and urea are statistically 
-  %indistinguishable. However, it's possible that they may diverge on longer 
-  %timescales due to differences in their curvature. 
-%  Similarly, methanol's MD MSD 
-%  is nearly linear while the MSDDM prediction is curving downward implying that it
-%  may underestimate the MSD on longer timescales.
-
-% BJC: alt to next paragraph
-%  We hypothesize that the predicted MSD of acetic acid is severely over-estimated
-%  most likely due to under-estimation of hop anti-correlation ($H$ too high) in 
-%  addition to an over-estimate of its hop lengths ($\sigma$ and $\alpha_h$ too high). 
-%  Acetic acid's predicted MSD actually lies just within the lower bound of urea's MD
-%  MSD 1$\sigma$ confidence interval, but lower than the prediction of the MSDDM for 
-%  urea. In all states, the degree of anti-correlation between acetic acid's hops is 
-%  higher than urea's (lower $H$) which is consistent with a lower predicted MSD. Although
-%  consistent, based on the curvature in Figure~\ref{fig:ACH_msddm}, and difficulties
-%  parameterizing $H$, it is possible that we under-estimated hop anti-correlation. 
-%  The length of acetic acid's hops and weight on the tails of the hop length 
-%  distribution ($\sigma$ and $\alpha_h$ respectively) are greater than or equal to 
-%  urea's which is consistent with a higher predicted MSD. There is also the strong 
-%  possibility that the over-estimate is a consequence of lumping together all of 
-%  acetic acid's transitional hops into a single correlated distribution.
 
   The predicted MSD of acetic acid is severely over-estimated primarily due to
-  under-estimation of hop anti-correlation ($H$ too high) and an over-estimate of
-  its hop lengths ($\sigma$ and $\alpha_h$ too high). Acetic acid's predicted MSD
-  actually lies just within the lower bound of urea's MD MSD 1$\sigma$ confidence
-  interval, but lower than the prediction of the MSDDM for urea. As stated earlier,
-  most of a solute’s motion modeled by the MSDDM is due to displacements during 
-  state transitions. Acetic
-  acid has a transitional Hurst parameter close to urea’s and transitional $\sigma$
-  and $\alpha_h$ values that are higher than urea’s. The primary reason that the MSDDM
-  predictions for acetic acid's MSD are lower than urea's appears to be because of
-  higher hop anti-correlation (lower $H$) in all states, including transitions. 
-  There is also the strong possibility that the over-estimate is a consequence of
-  lumping together all of acetic acid’s transitional hops into a single correlated
-  distribution.
+  under-estimation of hop anti-correlation ($H$ too high) and an over-estimate
+  of its hop lengths ($\sigma$ and $\alpha_h$ too high). Acetic acid's
+  predicted MSD actually lies just within the lower bound of urea's MD MSD
+  1$\sigma$ confidence interval, but lower than the prediction of the MSDDM for
+  urea. As stated earlier, most of a solute’s motion modeled by the MSDDM is
+  due to displacements during state transitions. Acetic acid has a transitional
+  Hurst parameter close to urea’s and transitional $\sigma$ and $\alpha_h$
+  values that are higher than urea’s. The primary reason that the MSDDM
+  predictions for acetic acid's MSD are lower than urea's appears to be because
+  of higher hop anti-correlation (lower $H$) in all states, including
+  transitions. There is also the strong possibility that the over-estimate is
+  a consequence of lumping together all of acetic acid’s transitional hops into
+  a single correlated distribution.
 
@@
   \caption{In most cases, the magnitude of the MSD curves predicted by the
-  MSDDM agree well with those generated from MD simulations. The predicted MSD
-  curves of urea and ethylene glycol lie within the 1$\sigma$ confidence 
-  intervals of MD for all time lags. Methanol over-predicts the MSD at small
-  time lags and acetic acid grossly over-predicts the MSD at all time lags.
-  Like the anomalous diffusion model, the MSDDM doesn't fully capture the 
-  curvature of the MD MSD curves. }\label{fig:msddm_performance}
+	  MSDDM agree well with those generated from MD simulations. The
+	  predicted MSD curves of urea and ethylene glycol lie within the
+	  1$\sigma$ confidence intervals of MD for all time lags. Methanol
+	  over-predicts the MSD at small time lags and acetic acid grossly
+	  over-predicts the MSD at all time lags.  Like the AD approach models,
+	  the MSDDM doesn't fully capture the curvature of the MD MSD curves.
+	  }\label{fig:msddm_performance}
   \end{figure}
 
-%MRS6: even if the MSD is well predicted, if the trajectories look different, can it really be a useful model?
-I.e.
-is one getting the right answer for the wrong reasons?
-What does it mean if MSD's are good, but the dwell times are not great?
   Despite relatively good predictions of the MD MSD, qualitative mismatch
@@
   realizations of the MSDDM for each solute and compared them to MD in
-  Figure~\ref{fig:msddm_eyetest}. There is little evidence of trapping behavior or
-  large hops. There are two reasons for this behavior. First, the width of 
+  Figure~\ref{fig:msddm_eyetest}. There is little evidence of trapping behavior
+  or large hops. There are two reasons for this behavior. First, the width of
   hop length distributions are much smaller than those of the AD model. Closer
-  examination of the characteristic MD trajectories shown in Figure~\ref{fig:solute_trajectories} 
-  reveal that hops tend to be an accumulation of a series of hops in the same direction.
-  All of the hops in the MSDDM are negatively correlated which prevents this from happening.
-  The second reason is a consequence of using a single hop length distribution 
-  for transitions. This was necessary because we could not collect enough data
-  to fit all of the possible transition distributions and because we could not
-  correlate emissions coming from different hop distributions. 
-  Many transitions occur between two trapped states where the 
-  transitional hops are actually very small. Our model ignores this physical 
-  restriction which can cause the solute to drift rather than stay trapped.
+  examination of the characteristic MD trajectories shown in
+  Figure~\ref{fig:solute_trajectories} reveal that hops tend to be an
+  accumulation of a series of hops in the same direction. All of the hops in
+  the MSDDM are negatively correlated which prevents this from happening. The
+  second reason is a consequence of using a single hop length distribution for
+  transitions. This was necessary because we could not collect enough data to
+  fit all of the possible transition distributions and because we could not
+  correlate emissions coming from different hop distributions. Many
+  transitions occur between two trapped states where the transitional hops are
+  actually very small. Our model ignores this physical restriction which can
+  cause the solute to drift rather than stay trapped.
 
@@
   \caption{Realizations of the MSDDM for each solute (blue) do not reproduce
-  the hopping and trapping behavior observed in our MD simulations (black). 
-  The trajectories are qualitatively similar to what one might expect for 
-  Brownian motion. 
-  %Note that 
-  %the length of the realizations are equal to the length of the equilibrated 
-  %portion of the MD trajectories for each solute.
+	  the hopping and trapping behavior observed in our MD simulations
+	  (black).  The trajectories are qualitatively similar to what one
+	  might expect for Brownian motion. 
   	  }\label{fig:msddm_eyetest}
@@
 
-% BJC6: I removed these because I think it doesn't add much. Could add a bit 
-% more to the conclusions.
-%  The MSDDM suffers similar shortcomings to the AD model. First, curvature 
-%  on long timescales due to positional anti-correlation may result in 
-%  underestimates of the MSD at large time lags. As suggested earlier, truncating
-%  the positional autocorrelation function may help solve this issue. Second, 
-%  parameterization can be challenging. In addition to possibly poor estimates 
-%  of the Hurst parameter, we made the simplifying assumption that we could lump
-%  all transitional hops into a single distribution. While this appears to work
-%  in most cases, it is the source of qualitative mismatches between MSDDM
-%  realizations and MD simulation trajectories and it may be the source of the 
-%  over-estimate of acetic acid's MSD.
-%  
-%  The MSDDM offers mechanistic insight and, in 3 out of 4 cases, gives reasonable
-%  predictions of solute MSDs. To successfully apply the model, one must know 
-%  representative discrete states beforehand or apply some technique to identify
-%  them. At the very least, we can used the MSDDM to obtain a detailed quantitative
-%  picture of dynamics within each state in terms of the magnitude of their 
-%  fluctuations and correlation with previous motion. If we have confidence in
-%  their predictive ability, then we can project solute trajectories out to 
-%  macroscopic timescales and estimate macroscopic observables such as solute 
-%  flux and selectivity.
-
   \subsection{Solute Flux and Selectivity}\label{section:mfpt}
@@
   We used the one mode sFBMcut (see Table~\ref{table:anomalous_models}) AD
-  model in order to demonstrate how one can use its realizations in order 
-  to calculate the flux (see section~\ref{method:mfpt}) of solutes given 
-  model parameters extracted from MD simulations. The one mode sFBMcut model
+  model in order to demonstrate how one can use its realizations in order to
+  calculate the flux (see section~\ref{method:mfpt}) of solutes given model
+  parameters extracted from MD simulations. The one mode sFBMcut model
   generates predictions similar to the one mode sFLMcut model at a lower
-  computational cost. We do not consider the two mode AD model because it 
-  has a broken correlation structure and we do not consider the MSDDM because
-  its realizations do not display the expected hopping and trapping behavior.
-
-  It is computationally infeasible to simulate trajectories long enough that they
-  traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
-  LLC membrane synthesized with the monomer in this work was 7$\mu$m thick. Using
-  24 cores to simulate trajectory realizations in parallel, it takes on the order 
-  of 1 day to simulate 10000 sFBMcut realizations of solutes traversing a 50 nm pore.
-  The RAM requirements and performance scales greater than linearly and thus would
-  take an infeasible amount of memory and time to simulate transport through a pore
-  over 100 times longer. One could improve performance significantly by simulating 
-  less trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting 
-  Information, we determined that one can simulate as few as 100 sFBMcut realizations
-  in order to parameterize Equation~\ref{eqn:flux_decay}. For better precision, we 
-  recommend simulating at least 1000 realizations. However, even with an order of 
-  magnitude decrease in number of trajectories, it is still infeasible to simulate
-  experimental-length pores.
-
-  We used simulated trajectories which traverse computationally-reasonable length
-  pores in order to construct an empirical model which one can use to estimate 
-  particle flux for arbitrary length pores. We fit Equation~\ref{eqn:passage_times}
-  to the empirical distribution of first passage times in Figure~\ref{fig:fpt_distributions}
-  and used the expected value of the analytical equation to calculate flux from 
-  Equation~\ref{eqn:hill_relation}. As shown in Figure~\ref{fig:flux_curves_ad}, 
-  the flux appears to scale according to a power law of the form:
+  computational cost. We do not consider the two mode AD model because it has a
+  broken correlation structure and we do not consider the MSDDM because its
+  realizations do not display the expected hopping and trapping behavior.
+
+  It is computationally infeasible to simulate trajectories long enough that
+  they traverse the length of a macroscopic pore. To date, the thinnest
+  H\textsubscript{II} LLC membrane synthesized with the monomer in this work
+  was 7$\mu$m thick. Using 24 cores to simulate trajectory realizations in
+  parallel, it takes on the order of 1 day to simulate 10000 sFBMcut
+  realizations of solutes traversing a 50 nm pore. The RAM requirements and
+  performance scales greater than linearly and thus would take an infeasible
+  amount of memory and time to simulate transport through a pore over 100 times
+  longer. One could improve performance significantly by simulating less
+  trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supplemental
+  Material, we determined that one can simulate as few as 100 sFBMcut
+  realizations in order to parameterize Equation~\ref{eqn:flux_decay}. For
+  better precision, we recommend simulating at least 1000 realizations.
+  However, even with an order of magnitude decrease in number of trajectories,
+  it is still infeasible to simulate experimental-length pores.
+
+  We used simulated trajectories which traverse computationally-reasonable
+  length pores in order to construct an empirical model which one can use to
+  estimate particle flux for arbitrary length pores. We fit
+  Equation~\ref{eqn:passage_times} to the empirical distribution of first
+  passage times in Figure~\ref{fig:fpt_distributions} and used the expected
+  value of the analytical equation to calculate flux from
+  Equation~\ref{eqn:hill_relation}. As shown in
+  Figure~\ref{fig:flux_curves_ad}, the flux appears to scale according to a
+  power law of the form:
   \begin{equation}
@@
   \end{subfigure}
-  \caption{(a) The distributions of first passage times generated from the sFBMcut model
-  fit well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
-  solutes in Figure~\ref{S-fig:ad_fpt_fits} of the Supplemental Material. (b) The 
-  single particle flux measured by the sFBMcut AD model decays with increasing pore 
-  length. The rankings of solute fluxes are consistent with the MSDs predicted by each
-  model. We fit the single particle solute flux versus pore length, $L$, to a power law
-  function of the form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
+  \caption{(a) The distributions of first passage times generated from the
+	  sFBMcut model fit well to Equation~\ref{eqn:passage_times}. We show
+	  similar fits for the remaining solutes in
+	  Figure~\ref{S-fig:ad_fpt_fits} of the Supplemental Material. (b) The
+	  single particle flux measured by the sFBMcut AD model decays with
+	  increasing pore length. The rankings of solute fluxes are consistent
+	  with the MSDs predicted by each model. We fit the single particle
+	  solute flux versus pore length, $L$, to a power law function of the
+	  form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
   }\label{fig:flux_curves}
@@
 
-  %BJC6: could move this paragraph to supporting
-  %MRS7: Could push more to supporting.  I think you just need to state that you ran with X number, as determined in the supporting, but because cheap did 10K for the non-MSDDM models.
-  %BJC7: Now that MSDDM is gone, and I have data for 10,000 sFBMcut trajectories, I added 
-  % a sentence to paragraph 2 before this one pointing to the SI.
-%  We determined that it is only necessary to simulate 1000 realizations of each model
-%  in order to parameterize Equation~\ref{eqn:flux_decay}. We used 10000 trajectory
-%  realizations in order to generate each point in Figure~\ref{fig:flux_curves_ad}, 
-%  however, in Figure~\ref{S-fig:flux_curve_sensitivity} of the Supplemental Material,
-%  we show that one can still show statistically significant differences in solute 
-%  flux, with minimal change to the mean flux values, using as few as 100 trajectory
-%  realizations. For better precision, we recommend simulating at least 1000 realizations. 
-%  Since the computational cost of the MSDDM is greater than the AD model, we generated
-%  each point of the flux curves in Figure~\ref{fig:flux_curves_msddm} using only 1000
-%  realizations at each pore length.
-
-  The scaling of solute flux with pore length is primarily influenced by anti-correlation
-  between solute hops. In Figure~\ref{fig:beta}a, we show that $\beta$ is inversely 
-  related to the Hurst parameter. This makes intuitive sense since higher degrees of
-  anti-correlation should slow the rate at which solutes cross the membrane pore. 
-  When we remove anti-correlation between hops (set $H$=0.5), the length dependence 
-  becomes the same for all solutes, dropping to a value just below 2. This also 
-  implies that hop lengths and dwell times do not affect length dependence since 
-  each solute exhibits different hopping and trapping behavior yet are all parameterized
-  by the same value of $\beta$ when $H$=0.5.
-  %BJC7: is above argument enough to get rid of following sentence (and associated bar in the Figure)?
-  We further verified this claim by removing hop anti-correlation and setting all 
-  dwell times equal to one timestep, effectively simulating Brownian motion.
-  The length dependence remains unchanged.
+  The scaling of solute flux with pore length is primarily influenced by
+  anti-correlation between solute hops. In Figure~\ref{fig:beta}a, we show that
+  $\beta$ is inversely related to the Hurst parameter. This makes intuitive
+  sense since higher degrees of anti-correlation should slow the rate at which
+  solutes cross the membrane pore. When we remove anti-correlation between
+  hops (set $H$=0.5), the length dependence becomes the same for all solutes,
+  dropping to a value just below 2. This also implies that hop lengths and
+  dwell times do not affect length dependence since each solute exhibits
+  different hopping and trapping behavior yet are all parameterized by the same
+  value of $\beta$ when $H$=0.5. We further verified this claim by removing
+  hop anti-correlation and setting all dwell times equal to one timestep,
+  effectively simulating Brownian motion.  The length dependence remains
+  unchanged.
 
@@
   % use c_parameters3.py
-  %BJC7: I could plot bars with the MSD of each solute to show that trend is same.
   \vspace{-0.25cm}
@@
   \vspace{-.5cm}
-  %MRS8: top figure is very confusing (also, I see a check in the urea green bar?) 
-  \caption{(a) Increased anti-correlation between hops (decreased $H$) appears to 
-  increase the length-dependence of solute flux (higher $\beta$) for the sFBMcut model.
-  (b) If we remove anti-correlation, by setting $H$=0.5, the length dependence parameter
-  drops to a value near 2. When we remove hop anti-correlation and dwell times between
-  hops, effectively simulating Brownian motion, the $\beta$ parameter stays near 2. 
-  This suggests that $\beta$ does not depend on dwell times (parameterized by $\alpha$
-  and $\lambda$). (c) As solute flux increases, the scaling of the flux 
-  curves, $A$, increases (compare ranking with Figure~\ref{fig:flux_curves_ad}).
-  (d) Physical processes which increase the rate of solute displacement 
-  result in larger values of $A$. To test the dependence of $A$ on $\alpha$, $\sigma$, 
-  $H$ and $\lambda$, we chose a single set of parameters, representative of solutes
-  parameterized by the sFBMcut AD model, and generated realizations of the
-  model by varying each parameter independently about the same base parameter set. 
+  \caption{(a) Increased anti-correlation between hops (decreased $H$) appears
+	  to increase the length-dependence of solute flux (higher $\beta$) for
+	  the sFBMcut model.  (b) If we remove anti-correlation, by setting
+	  $H$=0.5, the length dependence parameter drops to a value near 2.
+	  When we remove hop anti-correlation and dwell times between hops,
+	  effectively simulating Brownian motion, the $\beta$ parameter stays
+	  near 2.  This suggests that $\beta$ does not depend on dwell times
+	  (parameterized by $\alpha$ and $\lambda$). (c) As solute flux
+	  increases, the scaling of the flux curves, $A$, increases (compare
+	  ranking with Figure~\ref{fig:flux_curves_ad}).  (d) Physical
+	  processes which increase the rate of solute displacement result in
+	  larger values of $A$. To test the dependence of $A$ on $\alpha$,
+	  $\sigma$, $H$ and $\lambda$, we chose a single set of parameters,
+	  representative of solutes parameterized by the sFBMcut AD model, and
+	  generated realizations of the model by varying each parameter
+	  independently about the same base parameter set. 
 	  % Therefore, the middle bars for these four 4 parameters are 
@@
 	  Decreased dwell times (increased $\alpha$), increased hop lengths (increased
-  $\sigma$), and a lower cut-off to the dwell time distribution (increased $\lambda$)
-  lead to increases in $A$. 
+	  $\sigma$), and a lower cut-off to the dwell time distribution
+	  (increased $\lambda$) lead to increases in $A$. 
 	  %$A$ responds linearly to increases in $\sigma$ and $\lambda$
-  and non-linearly to $\alpha$.
-  The data suggests that the $A$ parameters do not depend on hop anti-correlation ($H$).
+	  and non-linearly to $\alpha$.  The data suggests that the $A$
+	  parameters do not depend on hop anti-correlation ($H$).
  	  }\label{fig:beta}
@@
 
-%  Parameters represented by physical processes which act to modify the rate at 
-%  which solutes move through the membrane pores will affect the scaling pre-factor
-%  of the solute flux curves ($A$).
-
   Dwell times and hop lengths directly modify the rate at which solutes move 
   through the membrane pores and are reflected in the scaling pre-factor of
-  the solute flux curves, $A$. Comparison of Figure~\ref{fig:beta}b with 
+  the solute flux curves, $A$. Comparison of Figure~\ref{fig:c_parameters} with 
   Figure~\ref{fig:flux_curves_ad} reveals that the ranking of the $A$ parameters
-  is consistent with the ranking of solute flux. In Figure~\ref{fig:beta}c we
+  is consistent with the ranking of solute flux. In Figure~\ref{fig:c_influence} we
   demonstrate that decreasing dwell times (increasing $\alpha$), cutting off 
@@
   hop lengths (increasing $\sigma$) independently lead to an increase in $A$. 
-  Figure~\ref{fig:beta}c also suggests that $A$ is not dependent on hop 
+  Figure~\ref{fig:c_influence} also suggests that $A$ is not dependent on hop 
   anti-correlation ($H$).
 
-  The power law decay of the flux with pore length implies the following relationship
-  for selectivity via substitution of Equation~\ref{eqn:flux_decay} into 
-  Equation~\ref{eqn:selectivity}:
+  The power law decay of the flux with pore length implies the following
+  relationship for selectivity via substitution of
+  Equation~\ref{eqn:flux_decay} into Equation~\ref{eqn:selectivity}:
   \begin{equation}
@@
 
-  \caption{The selectivity between pairs of species changes monotonically with pore length. 
-  The strength of dependence on pore length depends on the difference between $\beta$ values.
-  Largest differences in solute flux result in high selectivites at any pore length.
-  This membrane may be a good candidate for the separation of ethylene glycol from acetic
-  acid. Ethylene glycol has the lowest $\beta$ value while acetic acid has the second highest, 
-  leading to strong length dependence. Ethylene glycol also has the highest flux and acetic acid
-  has the lowest resulting in relatively high selectivities independent of pore length.}
+  \caption{The selectivity between pairs of species changes monotonically with
+	  pore length. The strength of dependence on pore length depends on
+	  the difference between $\beta$ values. The largest differences in solute
+	  flux result in high selectivites at any pore length. This membrane
+	  may be a good candidate for the separation of ethylene glycol from
+	  acetic acid. Ethylene glycol has the lowest $\beta$ value while
+	  acetic acid has the second highest, leading to strong length
+	  dependence. Ethylene glycol also has the highest flux and acetic acid
+	  has the lowest resulting in relatively high selectivities independent
+	  of pore length.}
   \label{fig:selectivity}
@@
 
-  In Figure~\ref{fig:selectivity}, we plot Equation~\ref{eqn:selectivity_ratio} for pore
-  lengths ranging from those studied in Figure~\ref{fig:flux_curves_ad} to macroscopic-length
-  pores. For the same degree of hop anti-correlation, as is the case for uncorrelated motion, 
-  selectivity depends on solute hop lengths and dwell times ($A$). For $(A_i / A_j)=1$, LLC
-  membranes will be more selective towards passage of solutes with less anti-correlated hopping
-  behavior (lower $\beta$). The selectivity towards solutes with less length dependent flux
-  increases with membrane thickness. 
-  %BJC8: modified
-  In most cases, the length dependence of selectivity plateaus near or within the range of 
-  experimentally-accessible membrane thicknesses. Therefore, from a practical standpoint, 
-  one should not expect significant changes in selectivity by varying LLC membrane thickness.
-
-%  before  which implies that a coating of LLC membrane with a thickness on the 
-%  order of those already made experimentally should be sufficiently 
-%  optimal.
-
-  %MRS8: IMPORTANT POINT!
-  %MRS8: I would play up that there is absolutely no way one could figure this out 
-  %MRS8: from looking at the molecules, or the pores, or even the MD trajectories alone.
-  %MRS8: There's a lot of complex interplay here that has the potentially to really lead to interesting 
-  %MRS8: separations. Even if the models aren't quite right, they show how such selectivtiy CAN arise.
-  %BJC8: added a new paragraph after this one.
+  In Figure~\ref{fig:selectivity}, we plot Equation~\ref{eqn:selectivity_ratio}
+  for pore lengths ranging from those studied in
+  Figure~\ref{fig:flux_curves_ad} to macroscopic-length pores. For the same
+  degree of hop anti-correlation, as is the case for uncorrelated motion,
+  selectivity depends on solute hop lengths and dwell times ($A$). For $(A_i /
+  A_j)=1$, LLC membranes will be more selective towards passage of solutes with
+  less anti-correlated hopping behavior (lower $\beta$). The selectivity
+  towards solutes with less length dependent flux increases with membrane
+  thickness. In most cases, the length dependence of selectivity plateaus near
+  or within the range of experimentally-accessible membrane thicknesses.
+  Therefore, from a practical standpoint, one should not expect significant
+  changes in selectivity by varying LLC membrane thickness.
 
@@
 
-  The insights into flux and selectivity provided by our time series modeling approach
-  could not be drawn easily by simply observing solute motion, the structure of the 
-  membrane nanopores, or even the solute trajectories extracted from the MD
-  simulations. Differences in solute MSDs alone do not fully explain the trends and 
-  magnitudes of the selectivities shown in Figure~\ref{fig:selectivity}.
-  Complex interplay between membrane constituents and solutes with varying
-  chemical functionality lead to diverse solute behavior. Even if our model is 
-  not perfect, it provides clear logic behind the mechanisms leading to selective
-  behavior which is very important for design. We hope this type of analysis can
-  be leveraged to explore new, interesting and complex separations problems.
-
-  %In both case, selectivity is enhanced as the pore 
-  %length increases which comes at the cost of lower solute flux, a phenomenon 
-  %ubiquitous in polymer separations membranes.~\cite{geise_water_2011}
-
-%  Ethylene glycol shows the least length dependent flux, likely because
-%  it spends the majority of its time in the pores (see Figure~\ref{fig:AD_mode_occupation}).
-%  %It also shows reasonable selectivity of Urea over acetic acid.  
-%  Ethylene glycol has the highest $c$ value and the lowest $\beta$ value. The high
-%  value of $c$ itself greatly enhances its selective passage. Even more importantly,
-%  the relatively large difference between its $\beta$ value and those of methanol 
-%  and acetic acid give rise to a strong pore length dependence. The selectivity is
-%  enhanced as the pore length increases at the cost of lower solute flux, a 
-%  phenomenon ubiquitous in polymer separations membranes.~\cite{geise_water_2011}
+  The insights into flux and selectivity provided by our time series modeling
+  approach could not be drawn easily by simply observing solute motion, the
+  structure of the membrane nanopores, or even the solute trajectories
+  extracted from the MD simulations. Differences in solute MSDs alone do not
+  fully explain the trends and magnitudes of the selectivities shown in
+  Figure~\ref{fig:selectivity}. Complex interplay between membrane
+  constituents and solutes with varying chemical functionality lead to diverse
+  solute behavior. Even if our model is not perfect, it provides clear logic
+  behind the mechanisms leading to selective behavior which is very important
+  for design. We hope this type of analysis can be leveraged to explore new,
+  interesting and complex separations problems.
 
@@
   We have tested two different mathematical frameworks for describing solute
-  motion by applying them to an H\textsubscript{II} phase LLC membrane. The values
-  obtained for the parameters when fitting the models to the time series data 
-  offer important mechanistic insight on the molecular details of transport.
-  Subordinated fractional Brownian and L\'evy motion have a strong theoretical 
-  foundation in the anomalous diffusion literature. Our single mode model
-  quantifies and allows comparison of the hopping and trapping behavior 
-  among solutes. A two mode model that describes dynamics based on whether
-  a solute is in or out of the pore region allows us to break down individual
-  solute motion into the two distinct regimes and we showed that solute motion is
-  clearly restricted while in the tail region. Our Markov state-dependent dynamical
-  model uses explicitly defined trapping mechanisms and gives a nice description 
-  of transitions between these observed states, the equilibrium distribution of 
-  solutes among states as well as the type of stochastic behavior shown in each 
-  state.
-
-%  In their current state, one should use the predictions of our models with caution.
+  motion by applying them to an H\textsubscript{II} phase LLC membrane. The
+  values obtained for the parameters when fitting the models to the time series
+  data offer important mechanistic insight on the molecular details of
+  transport. Subordinated fractional Brownian and L\'evy motion have a strong
+  theoretical foundation in the anomalous diffusion literature. Our single mode
+  AD model quantifies and allows comparison of the hopping and trapping behavior
+  among solutes. A two mode model that describes dynamics based on whether a
+  solute is in or out of the pore region allows us to break down individual
+  solute motion into the two distinct regimes and we showed that solute motion
+  is clearly restricted while in the tail region. Our Markov state-dependent
+  dynamical model uses explicitly defined trapping mechanisms and gives a nice
+  description of transitions between these observed states, the equilibrium
+  distribution of solutes among states as well as the type of stochastic
+  behavior shown in each state.
+
   Although large portions of the MSDs predicted by our models fall close to or
-  within the 1$\sigma$ confidence intervals of MD, it is not always for physically
-  accurate reasons. Qualitatively, MSDDM trajectories do not display the same hopping
-  and trapping behavior shown by MD trajectories. Frequent transitions drawn from a
-  single, relatively broad transition emission distribution prevent long periods of
-  immobility. The most obvious solution to this would be to generate individual emission
-  distributions for each type of transition, but this would require orders of magnitude
-  more data or more prior assumptions about the distributions.
-  This approach is further complicated by the need to make correlated draws
-  from a fractional L\'evy process with a frequently changing distribution width. 
-  A possible simplification could be to assume that correlation is lost every time a
-  state transition occurs.
-%  AD model realizations show appropriate qualitative behavior, but the persistent 
-%  curvature of the computed MSD curves, due to the correlation structure of fractional 
-%  motion, under-estimate the MD MSD curves which appear to be trending towards linear
-%  on $\mu$s timescales. In the future, we could address this by implementing a truncation
-%  to the positional auto-correlation function.
-
-  %MRS8: ``the AD model'' vs approach, since it's multiple models.
+  within the 1$\sigma$ confidence intervals of MD, it is not always for
+  physically accurate reasons. Qualitatively, MSDDM trajectories do not display
+  the same hopping and trapping behavior shown by MD trajectories. Frequent
+  transitions drawn from a single, relatively broad transition emission
+  distribution prevent long periods of immobility. The most obvious solution to
+  this would be to generate individual emission distributions for each type of
+  transition, but this would require orders of magnitude more data or more
+  prior assumptions about the distributions. This approach is further
+  complicated by the need to make correlated draws from a fractional L\'evy
+  process with a frequently changing distribution width. A possible
+  simplification could be to assume that correlation is lost every time a state
+  transition occurs.
+
   Although the AD approach generates qualitatively accurate trajectories and
-  predicts MSDs near or within the 1$\sigma$ confidence interval of our
-  MD simulations, the curvature of the predicted MSDs does not appear to be consistent
-  with the MD simulations. The MSD curves calculated from MD simulations 
-  appear to straighten out on long timescales while those predicted
+  predicts MSDs near or within the 1$\sigma$ confidence interval of our MD
+  simulations, the curvature of the predicted MSDs does not appear to be
+  consistent with the MD simulations. The MSD curves calculated from MD
+  simulations appear to straighten out on long timescales while those predicted
   AD models continuously curve. This is because pure fractional Brownian motion
-  features hop correlation that persists indefinitely. We may be able to address
-  this by truncating the positional autocorrelation function, allowing 
+  features hop correlation that persists indefinitely. We may be able to
+  address this by truncating the positional autocorrelation function, allowing
   correlation to diminish on the 100 ns timescale as suggested by the physical
@@
 
-  We demonstrated how one could use the one mode AD model in order to to determine
-  macroscopic flux and selectivity. We showed that, when using the AD model, 
-  solute flux decreases with pore length at a rate faster than pure 
+  We demonstrated how one could use the one mode AD model in order to to
+  determine macroscopic flux and selectivity. We showed that, when using the AD
+  model, solute flux decreases with pore length at a rate faster than pure
   Brownian motion due to anti-correlation between hops. We used the ratio of
@@
 
-  % BJC5: I'm not sure if this paragraph belongs here. Or if it should go at end
-  % of previous section. Or just eliminate. What do you think?  \
-  % BJC6: took out for now since I was questioning it. Can add back if reviewers ask about these considerations.
-  %MRS7: yeah, leave out for now.
-%  Of course, our approach to modeling LLC membrane selectivity neglects a number
-%  of factors that influence real-world aqueous membrane separations. The most 
-%  glaring is that we neglected convective flux which should work to increase 
-%  overall solute flux and lower selectivity (see Equation ~\ref{eqn:solute_flux}).
-%  Defects in the pore structure will have a strong influence on solute flux which
-%  may exacerbate the length dependence of flux. Even in a perfectly structured 
-%  membrane, the barrier to pore entry from the bulk solution will have its own 
-%  influence on experimentally observed selectivities. This energetic barrier can 
-%  be made even worse by foulants deposited on the membrane's surface. Therefore,
-%  our predictions should be primarily used to identify the most promising types
-%  of selective separations for an H\textsubscript{II} LLC membrane made from a 
-%  specific monomer.
-
   Despite their shortcomings, our mathematical models help us think about how
   to design LLC monomers for solute-specific separations by forcing us to think
-  in terms of controlling solute transport. The anomalous diffusion modeling approach is 
-  quite flexible because it does not require knowledge of specific trapping 
-  mechanisms. Screening a set of solutes and applying the anomalous diffusion 
-  %MRS8: I wonder if the 2 mode model can be considered a intermediate - a bit of structural information is involved.
-  approach can help uncover trapping mechanisms by forcing the scientist to 
-  identify features common to solutes with long or short hop lengths and dwell
-  times. The MSDDM is a powerful way to characterize explicit trapping mechanisms.
-  It clearly partitions a trajectory into discrete mechanisms and quantifies their
-  relative dominance in the real system. For example, it is clear that 
-  sodium ion association is primarily responsible for trapping urea while 
-  hydrogen bonding dominates ethylene glycol. If one re-designs an LLC monomer
-  to eliminate one source of trapping, then high selectivities are possible.
-  Our models facilitate new ways of approaching complex separation problems.
+  in terms of controlling solute transport. The anomalous diffusion modeling
+  approach is quite flexible because it does not require knowledge of specific
+  trapping mechanisms. Screening a set of solutes and applying the anomalous
+  diffusion approach can help uncover trapping mechanisms by forcing the
+  scientist to identify features common to solutes with long or short hop
+  lengths and dwell times. The MSDDM is a powerful way to characterize explicit
+  trapping mechanisms. It clearly partitions a trajectory into discrete
+  mechanisms and quantifies their relative dominance in the real system. For
+  example, it is clear that sodium ion association is primarily responsible for
+  trapping urea while hydrogen bonding dominates ethylene glycol. If one
+  re-designs an LLC monomer to eliminate one source of trapping, then high
+  selectivities are possible. ur models facilitate new ways of approaching
+  complex separation problems.
 
@@
 
-  Detailed explanations and expansions upon the results and procedures mentioned in
-  the main text are described in the Supplemental Material. This information is
-  available free of charge via the Internet at http://pubs.acs.org.
+  Detailed explanations and expansions upon the results and procedures
+  mentioned in the main text are described in the Supplemental Material. This
+  information is available free of charge via the Internet at
+  http://pubs.acs.org.
 
@@
 
-  %MRS: add people who contributed non-author level ideas. 
-  %MRS3: add specific info for PRF and GAANN
-  %BJC3: I wrote GAANN as I did on the last paper which is what Rob Davis told me to do
-  This work was supported in part by the ACS Petroleum Research Fund grant \#59814-ND7
-  and the Graduate Assistance in Areas of National Need (GAANN)
-  fellowship which is funded by the U.S. Department of Education.
-  Molecular simulations were performed using the Extreme Science and
-  Engineering Discovery Environment (XSEDE), which is supported by National
-  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
+  This work was supported in part by the ACS Petroleum Research Fund grant
+  \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN)
+  fellowship which is funded by the U.S. Department of Education.  Molecular
+  simulations were performed using the Extreme Science and Engineering
+  Discovery Environment (XSEDE), which is supported by National Science
+  Foundation grant number ACI-1548562. Specifically, it used the Bridges
   system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
-  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
-  which is supported by the National Science Foundation (awards ACI-1532235 and
-  ACI-1532236), the University of Colorado Boulder, and Colorado State
-  University. The Summit supercomputer is a joint effort of the University of
-  Colorado Boulder and Colorado State University.
+  Supercomputing Center (PSC). This work also utilized the RMACC Summit
+  supercomputer, which is supported by the National Science Foundation (awards
+  ACI-1532235 and ACI-1532236), the University of Colorado Boulder, and
+  Colorado State University. The Summit supercomputer is a joint effort of the
+  University of Colorado Boulder and Colorado State University.
 
@@
 
-  \section*{TOC Graphic}
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=3.25in]{toc.pdf}
-  \end{figure}
+  % No TOC image in PRE
+  %\section*{TOC Graphic}
+
+  %\begin{figure}[!htb]
+  %\centering
+  %\includegraphics[width=3.25in]{toc.pdf}
+  %\end{figure}
 

### 2020-01-27 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Changed duplicate reference

@@
   \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
-  \caption{100 Independent Trajectories}\label{fig:N100}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
-  \caption{1000 Independent Trajectories}\label{fig:N1000}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
-  \caption{5000 Independent Trajectories}\label{fig:N5000}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
-  \caption{10000 Independent Trajectories}\label{fig:N10000}
+  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_URE.pdf}
+  \caption{urea}\label{fig:Nsensitivity_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_ACH.pdf}
+  \caption{acetic acid}\label{fig:Nsensitivity_ACH}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_GCL.pdf}
+  \caption{ethylene glycol}\label{fig:Nsensitivity_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_MET.pdf}
+  \caption{mehtanol}\label{fig:Nsensitivity_MET}
   \end{subfigure}
   \caption{Even using a small number of independent trajectories, one can
-  reliably calculate flux as a function of pore length. The uncertainty in
-  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
-  \end{figure}
+  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
+  the flux values decreases as we add more independent trajectories.
+  }\label{fig:flux_curve_sensitivity}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_URE.pdf}
+  \caption{urea}\label{fig:Asensitivity_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_ACH.pdf}
+  \caption{acetic acid}\label{fig:Asensitivity_ACH}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_GCL.pdf}
+  \caption{ethylene glycol}\label{fig:Asensitivity_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_MET.pdf}
+  \caption{mehtanol}\label{fig:Asensitivity_MET}
+  \end{subfigure}
+  \caption{Even using a small number of independent trajectories, one can
+  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
+  the flux values decreases as we add more independent trajectories.
+  }\label{fig:A_sensitivity}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_URE.pdf}
+  \caption{urea}\label{fig:betasensitivity_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_ACH.pdf}
+  \caption{acetic acid}\label{fig:betasensitivity_ACH}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_GCL.pdf}
+  \caption{ethylene glycol}\label{fig:betasensitivity_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_MET.pdf}
+  \caption{mehtanol}\label{fig:betasensitivity_MET}
+  \end{subfigure}
+  \caption{Even using a small number of independent trajectories, one can
+  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
+  the flux values decreases as we add more independent trajectories.
+  }\label{fig:beta_sensitivity}
+  \end{figure}
+
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
+%  \caption{100 Independent Trajectories}\label{fig:N100}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
+%  \caption{1000 Independent Trajectories}\label{fig:N1000}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
+%  \caption{5000 Independent Trajectories}\label{fig:N5000}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
+%  \caption{10000 Independent Trajectories}\label{fig:N10000}
+%  \end{subfigure}
+%  \caption{Even using a small number of independent trajectories, one can
+%  reliably calculate flux as a function of pore length. The uncertainty in
+%  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
+%  \end{figure}
   %MRS8: is there a way to make it easier to see the fact that the data is relatively independent of length?

### 2020-01-27 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Fixed missing reference
New figures and small edits

@@
 
-\title{Supporting Information: Capturing Subdiffusive Solute Dynamics and 
+\title{Supplemental Material: Capturing Subdiffusive Solute Dynamics and 
 Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
@@
   %versus 10000 of the AD model. 
-  In Figure~\ref{fig:flux_curve_sensitivity}, we
+  In Figures~\ref{fig:flux_curve_sensitivity}--~\ref{fig:beta_sensitivity}, we
   %justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
 %  model realizations to 
-  show that one only needs as few as 100 independent trajectory
-  realizations at each pore length in order to reliably fit Equation~\ref{eqn:passage_times}
-  to the passage time distributions.
+  show that one can reliably fit Equation~\ref{eqn:passage_times}
+  to the passage time distributions with as few as 100 independent trajectory
+  realizations at each pore length. For higher precision, we recommend using at least
+  1000 trajectories.
 
@@
   \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_MET.pdf}
-  \caption{mehtanol}\label{fig:Nsensitivity_MET}
+  \caption{methanol}\label{fig:Nsensitivity_MET}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{flux_curves_Asensitivity_MET.pdf}
-  \caption{mehtanol}\label{fig:Asensitivity_MET}
-  \end{subfigure}
-  \caption{Even using a small number of independent trajectories, one can
-  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
-  the flux values decreases as we add more independent trajectories.
+  \caption{methanol}\label{fig:Asensitivity_MET}
+  \end{subfigure}
+  \caption{The flux scaling parameter ($A$) can be reliably estimated using
+  as few as 100 independent realizations of the sFBMcut AD model. To estimate
+  $A$, we fit Equation~\ref{M-eqn:flux_decay} of the main text to a series of
+  flux measurements made with 10, 15, 20, 25, 30, 35, 40, 45 and 50 nm pores (see
+  Figure~\ref{M-fig:flux_curves_ad} of the main text).
   }\label{fig:A_sensitivity}
@@
   \includegraphics[width=\textwidth]{flux_curves_betasensitivity_MET.pdf}
-  \caption{mehtanol}\label{fig:betasensitivity_MET}
-  \end{subfigure}
-  \caption{Even using a small number of independent trajectories, one can
-  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
-  the flux values decreases as we add more independent trajectories.
+  \caption{methanol}\label{fig:betasensitivity_MET}
+  \end{subfigure}
+  \caption{Similar to $A$, the parameter which describes the scaling of solute
+  flux with pore length, $\beta$, can be reliably estimated using as few as 100
+  independent realizations of the sFBMcut AD model. We estimated $\beta$ and
+  $A$ simultaneously as described in Figure~\ref{fig:A_sensitivity}.
   }\label{fig:beta_sensitivity}

### 2020-01-28 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Changed duplicate reference
Fixed missing reference
UUpdate tex.

@@
   and solute flux, and thus solute selectivity, in macroscopic length pores.
+
   First, using anomalous diffusion theory, we show how solute dynamics can be
@@
   dwell times, hop lengths between dwells and correlation between hops. We 
-  explore two variations of the anomalous diffusion modelling approach. The first variation
+  explore two variations of the anomalous diffusion modeling approach. The first variation
   applies a single set of parameters to the solute displacements and the second
   applies two sets of parameters based on the solute's radial distance from the
-  closest pore center. Next, we generalize Markov state models, treating the
+  closest pore center.
+
+  Next, we generalize Markov state models, treating the
   configurational state of the system as a Markov process, each
-  of which having separate transport properties. For each state and transition
+  state of which has  
+  %MRS10:
+  %each having separate
+  distinct transport properties. For each state and transition
   between states, we parameterize the distribution and temporal correlation 
@@
   between MD and Markov state dependent model-generated trajectories may limit 
-  its usefulness. Finally, we demonstrate how one can use these models to 
+  its usefulness.
+
+  Finally, we demonstrate how one can use these models to 
   estimate flux of a solute across a macroscopic-length pore and, based on 
@@
   decrease a Q\textsubscript{I} phase membrane's permeability relative to the
-  H\textsubscript{II} phase, it is considerably easier to synthesize at
-  scale.~\cite{hatakeyama_nanoporous_2010}
+  H\textsubscript{II} phase, it is considerably easier to 
+  %MRS10: synthesis implies chemical synthesis, this is really assembly - but produce is more general. 
+  %synthesize 
+  produce 
+  at scale.~\cite{hatakeyama_nanoporous_2010}
 
@@
   Using a bottom-up modeling approach, we can parameterize single particle
-  behavior by extracting their trajectories from MD simulations and studying
+  behavior by extracting 
+  %MRS10: their is referring to behavior, which is singular - changing grammar.
+  %their 
+  particle
+  trajectories from MD simulations and studying
   the properties that have the greatest influence on solute dynamics. With this
@@
   uncertainties. Fortunately, there is an abundance of information encoded in
-  the complex solute trajectories. Into a model, we can incorporate fluctuations and
-  time-dependent correlations in solute position as well as the length of time
+  the complex solute trajectories. 
+  %MRS: moving clause out from top.
+  %Into a model, 
+  We can incorporate fluctuations and
+  time-dependent correlations in solute position 
+  %MRS added:
+  into transport models, 
+  as well as the length of time
   solutes are trapped. We can add further detail by integrating
@@
 
-  We constructed our first model by applying the rigorous theoretical
-  foundation already developed to describe the motion of particles exhibiting
+  We constructed our first model by applying the 
+  %MRS10: tweaked
+  existing
+  rigorous theoretical
+  foundation 
+  %already developed 
+  to describe the motion of 
+  particles 
+  %MRS10: added specificity
+  simulated at the atomistic level
+  %exhibiting
+  which exhibit
   non-Brownian, or anomalous, transport
@@
   radial distance from the closest pore center. This allows us to include
-  different dynamical behavior of solutes observed within the pore region
+  different dynamical behavior of solutes 
+  %MRS10: added, to show that this is informed by looking at the trajectories.
+  previously
+  observed within the pore region
   versus within the monomer tails.
 
-  Where applicable, the sFBM model provides a way to propagate information
+  %MRS10: tweaked, also made plural since multiple models are built.
+  %Where applicable, the sFBM model 
+  Where sufficiently close to observed data, these fitted sFBM models
+  provides a way to propagate information
   about solute trajectories gathered at the microsecond time scale to realistic
-  experimental time scales. It can also confirm the importance of assumed
+  experimental time scales. They can also confirm the importance of assumed
   solute-membrane interactions used to define the model's functional form, and
-  suggest missing components. It can help researchers formulate hypotheses to
+  suggest missing components. They can help researchers formulate hypotheses to
   explain why a certain set of parameters is characteristic to a specific
@@
   well as the equilibrium occupation of each trapping state.  It is possible to
-  use the two modelling approaches in tandem, the AD approach to identify
+  use the two modeling approaches in tandem, the AD approach to identify
   mechanisms, and the MSDDM to characterize mechanisms.
@@
   work: methanol, urea, ethylene glycol and acetic acid. In addition to moving
-  quickly, allowing them to extensively explore membrane structural space,
+  %MRS10: tweaked, may not be quick in absolute terms.
+  more 
+  quickly
+  than other solutes studied previously, 
+  allowing them to extensively explore membrane structural space,
   these solutes have a range of chemical functionality and experience each of
@@
   to collect ample data. We ran MD simulations using the leapfrog integrator with 
-  h-bonds constrained by the LINCS algorithm. We simulated a time step of 2 fs at
+  hydrogen bonds constrained by the LINCS algorithm. We simulated a time step of 2 fs at
   a pressure of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and
@@
   to a discrete power law distribution whose maximum likelihood $\alpha$ 
-  parameter we calculated by maximizing the likelihood function: 
+  parameter we calculated by maximizing the 
+  %MRS10: added for precision
+  log
+  likelihood function: 
   \begin{equation}
@@
   to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model.
-  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
+  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the 
+  %MRS10:
+  log 
+  likelihood function:~\cite{clauset_power-law_2009}
   \begin{equation}
@@
   We used the Python package \texttt{fbm} to generate exact simulations of FBM
+  %MRS10: add a reference to where your implementation can be found.
   and our own Python implementation of the algorithm by Stoev and Taqqu to
@@
   states with transitions between states defined by a transition probability
-  matrix, $T$, which describes the conditional probability of moving to a
+  matrix, $T$.  
+  %MRS10: split sentence for readability.
+  $T$ describes the conditional probability of moving to a
   specific state given the previously observed
@@
   with an atom if they are within 2.5 \AA~of each other, as determined in our
-  previous work~\cite{coscia_chemically_2019}
+  previous work.~\cite{coscia_chemically_2019}
 
@@
   \end{subfigure}
-  \caption{Representative trajectories generated from each solute exhibit hops
+  \caption{
+    %MRS10: added
+    Three
+    representative trajectories generated from each solute exhibit hops
 	  between periods of entrapment, characteristic of a CTRW. Solute
@@
   \caption{Using urea as an example, (a) the distribution of hop lengths can be
-	  fit by a Gaussian as well as a more general L\'evy stable
-	  distribution. The L\'evy stable distribution does a better job of
+	  fit by a Gaussian 
+          ``as well as'' is ambiguous, can mean ``in addition to'' or ``similar in quality to''
+          %as well as 
+          almost as well as
+          a more general L\'evy stable
+	  distribution, though the L\'evy stable distribution does a better job of
 	  capturing the heavier tails and increased density near 0. We explore
-	  models fit to both distributions since Gaussian hops are convenient
+	  models fit to both distributions, as Gaussian hops are more convenient
 	  to model. (b) The distribution of dwell times is fit well by a power
@@
   Urea and acetic acid appear to demonstrate satisfactory stationarity. The
-  shapes of their MSD curves are also very similar (see
+  shapes of 
+  %MRS10: which of the solutes does ``their'' refer to?  Be more explicit.
+  their MSD curves are also very similar (see
   Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).
@@
   parameterize AD models with all available data after the perceived
-  equilibration time. The MSD curves generated from the 1 and 2 mode models
+  equilibration time. The MSD curves generated from 
+  %MRS10: added
+  both 
+  %MRS10: more grammatically correct to say ``one and two'' instead of ``1 and 2''
+  the one and two mode models
   are overlayed with the MD simulated MSDs for comparison in
-  Figure~\ref{fig:anomalous_msds}. The associated parameters for the 1 and 2
+  Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
   mode models are presented in Figures~\ref{fig:1mode_parameters}
@@
 	  distributions to describe solute hop lengths. We assume the mean
-	  ($\mu$) to be zero for these distributions and there to be no
+	  ($\mu$) to be zero for these distributions and no
 	  skewness ($\beta = 0$) in the L\'evy stable distributions. High
@@
 	  autocorrelation function, $\gamma(H)$, to describe the degree of
-	  correlation between hops. Higher values of $H$ display closer to
-	  Brownian behavior.}\label{fig:1mode_parameters}
+	  correlation between hops. 
+          %MRS10: tweaked
+          Simulations with higher values of $H$ display behavior closer to
+	  the Brownian limit.}\label{fig:1mode_parameters}
   \end{figure}
@@
   to match the curvature of MD quite well, but closer examination reveals that
-  the MD MSD curve actually shifts from a sub-linear to a linear regime around
+  the MD MSD curve 
+  %MRS10: being a bit more cautious about claims.
+  %actually shifts 
+  may actually shift
+  from a sub-linear to a linear regime around
   500 ns.
@@
 
-  Turning first to the parameters of the one mode model, we can begin to break
+  %MRS10: tweak
+  %Turning first to 
+  Examining first
+  the parameters of the one mode model, we can begin to break
   down the trends in solute MSDs. The parameters belonging to ethylene glycol
-  and methanol are relatively similar which is consistent with their similar MD
-  MSDs. Relative to ethylene glycol, methanol tends to stay trapped for less
+  and methanol are relatively similar, which is consistent with their similar MD
+  MSDs
+  %MRS10: added
+  and qualitatively similar MD timeseries.
+  Relative to ethylene glycol, methanol tends to stay trapped for less
   time and takes larger hops but the most substantial difference is with
@@
   respectively) while ethylene glycol spends about 44\% of its time in the
-  tails. Urea and acetic acid's compact and flat structure allows it to more
+  tails. Urea and acetic acid's compact, flat structure allows it to more
   easily partition into the tails while ethylene glycol prefers the pore region
@@
   enough that it does not need to make larger jumps to escape traps.
+
+  %MRS10: A thought going through this - a diagram with a picture of
+  %the molecule pointing to features that promote certain behavior
+  %would be interesting here.  I would suggest waiting until we get
+  %reviews back, though.  You should get this submitted.
 
@@
   To create an MSDDM for each solute, we determined the state sequence associated
-  with each solute trajectory and then generated emission distributions of fluctuations
+  with each solute trajectory 
+  %MRS10: added for clarity to make sure people who how the state sequence was determined.
+  based on the geometric indicators of the states indicated in Table~\ref{table:states}.
+  and then generated emission distributions of fluctuations
   within each state as well as transitions between states. In theory, one could 
@@
   pronounced than that seen in the hop length distributions of the previous
-  section, therefore we did not consider the Gaussian case (see
+  section.  
+  %MRS10: break for clarity.
+  We therefore did not consider the Gaussian case (see
   Figure~\ref{fig:gaussian_levy_comparison}). The correlation structure
@@
   \end{subfigure}
+  %MRS10: Probably will need to make the font labels bigger in a revision.
  \caption{The parameters of the MSDDM are strong functions of trapping
@@
 	  influencing trapping mechanisms increases, the Hurst parameter, $H$,
-	  decreases. $H$ is highest during transitions between states (state
+	  decreases. $H$ is 
+          highest 
+          %MRS10
+          (closest to Brownian)
+          during transitions between states (state
 	  T). (b) As more trapping mechanisms simultaneously influence solutes,
@@
 
+  %MRS10: is it a good idea to say they are well-captured when we get results qualitatively different from MD later?
   The dynamics of urea, ethylene glycol and, to a lesser extent, methanol appear
@@
   fit all of the possible transition distributions and because we could not
+  %MRS10: my feeling is (to keep in the back of the mind) that we may be able to add some sort of 
+  %prior to fit the transition distributions.  Lots of distributions can be fit with low amounts of data
+  %if one makes enough assumptions about what the functional form of the distribution is. And we could
+  %presumaly come up with something reasonable. But that's for another time. 
   correlate emissions coming from different hop distributions. Many
@@
 	  (black).  The trajectories are qualitatively similar to what one
-	  might expect for Brownian motion. 
+	  might expect for Brownian motion
+          %MRS10: added for context
+          even though the MSDs are often similar to the atomistic systems.
   	  }\label{fig:msddm_eyetest}
@@
   H\textsubscript{II} LLC membrane synthesized with the monomer in this work
-  was 7$\mu$m thick. Using 24 cores to simulate trajectory realizations in
+  was 7$\mu$m thick. 
+  %MRS10: provide citation here for the fact of 7mum thick.
+  Using 24 cores to simulate trajectory realizations in
   parallel, it takes on the order of 1 day to simulate 10000 sFBMcut
@@
   \includegraphics[width=\textwidth]{beta_variations.pdf}
-  \caption{}\label{fig:beta_hurst}
+  \caption{}\label{fig:beta_variations}
   \end{subfigure}
@@
   \includegraphics[width=0.5\textwidth]{selectivity.pdf}
-
+  %MRS10: may need to move the legend out of the way if asked to in reviews, don't bother now.
   \caption{The selectivity between pairs of species changes monotonically with
@@
 	  the difference between $\beta$ values. The largest differences in solute
-	  flux result in high selectivites at any pore length. This membrane
+	  flux result in high selectivities at any pore length. This membrane
 	  may be a good candidate for the separation of ethylene glycol from
@@
   solute behavior. Even if our model is not perfect, it provides clear logic
-  behind the mechanisms leading to selective behavior which is very important
-  for design. We hope this type of analysis can be leveraged to explore new,
+  behind the mechanisms leading to selective behavior 
+  %MRS10: softened claim a bit - it hasn't been used for design yet.
+  %which is very important for design. 
+  which could significantly help illuminate any design choices.
+  We hope this type of analysis can be leveraged to explore new,
   interesting and complex separations problems.
@@
   scientist to identify features common to solutes with long or short hop
-  lengths and dwell times. The MSDDM is a powerful way to characterize explicit
+  lengths and dwell times. 
+  %MRS10: may want to mention a bit about the weakness of the methods (i.e. say something about what 
+  % can be done even given the lack of correlation structure), since it's in the conclusion.
+  The MSDDM is a powerful way to characterize explicit
   trapping mechanisms. It clearly partitions a trajectory into discrete
@@
   trapping urea while hydrogen bonding dominates ethylene glycol. If one
-  re-designs an LLC monomer to eliminate one source of trapping, then high
-  selectivities are possible. ur models facilitate new ways of approaching
+  re-designs an LLC monomer to eliminate one source of trapping, then 
+  %MRS10: tweaked 
+  %high
+  higher
+  selectivities 
+  may result.
+  %are possible. 
+  %Our 
+  The modeling approaches presented in this paper 
+  facilitate new ways of approaching
   complex separation problems.
@@
 % LocalWords:  bothmode todo eyetest Methanol's acid's subplots methanol's alt
-% LocalWords:  timestep pre selectivtiy foulants subfigures
+% LocalWords:  timestep pre selectivtiy foulants subfigures RWFs roman github
+% LocalWords:  al linkable nanopores

### 2020-01-28 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Update supporting info.
fixed supporting and PDFs.

@@
   \maketitle
+  %MRS10: be consistent on capitalization of section titles (And therefore table of contents)
   \tableofcontents
@@
   solutes in and out of the pore region stopped changing. The pore region is
-  defined as within 0.75 nm of the pore center. We've plotted the partition
+  defined as within 0.75 nm of the pore center. We plot the partition
   versus time in Figure~\ref{fig:equilibration} and indicated the chosen
@@
   different sized time steps.}\label{fig:counts}
+  %MRS10: be clear why the graph shows detailed balance in the caption.
   %MRS: would this be clearer to see if you plotted i-j/i+j for a relative error to see how different it is from symmetric jumps? 
@@
   When we use a pure power law distribution to parameterize the dwell time 
-  distributions of the 1 and 2 mode AD models, the MD MSDs are severely 
+  distributions of the one and two mode AD models, the MD MSDs are severely 
   under-predicted because we are incorporating dwell times on the order of 
@@
 
-  We validated both the 1 and 2 mode AD models with urea and acetic acid, since their
+  We validated both the one and two mode AD models with urea and acetic acid, since their
   trajectories appear stationary. The MSDs resulting from 1000 realizations of the AD
@@
   exponential cut-off. At long timescales, the MSD of urea is under-predicted 
-  for both the 1 and 2 mode models with the same true of acetic acid on short 
+  for both the one and two mode models with the same true of acetic acid on short 
   timescales. Without truncation of the power law distribution, the MD 
@@
 % LocalWords:  sFBMcut sFLMcut urea's timescale msddm fpt CDF mfpt cdf hurst
-% LocalWords:  decorrelate
+% LocalWords:  decorrelate nanopore FLM autocovariance evy undersampling Stoev
+% LocalWords:  undersampled URE timescales Nsensitivity Asensitivity
+% LocalWords:  betasensitivity

### 2020-01-28 Ben_Manuscripts/stochastic_transport/cover_letter.tex
update letter.
New figures and small edits
Tweaked formatting.

@@
 	interest to researchers who study complex dynamics in both structured
-	and amorphous soft materials. \\
+	and amorphous soft materials.
 
 	In this article, we use 5$\mu$s molecular dynamics (MD) simulations of
-	solutes moving through the pores of an inverted hexagonal phase
-	lyotropic liquid crystal (LLC) polymer membrane in order to
-	parameterize two different stochastic time series models capable of
-	predicting solute flux and selectivity on a macroscopic scale.
-	Realizations of both models quantitatively reproduce the mean squared
-	displacements (MSDs) exhibited by the solutes in our MD simulations. We then
-	demonstrate how we can use realizations orders of magnitude longer than
-	our MD simulations in order to predict solute flux and selectivity.
-	This is among the first studies to apply time series modeling
-	approaches in order to predict bulk materials properties. \\
+	solutes moving through the pores of an inverted hexagonal phase lyotropic
+	liquid crystal (LLC) polymer membrane in order to parameterize two different
+	stochastic time series models capable of predicting solute flux and selectivity
+	on a macroscopic scale.  Realizations of both models quantitatively reproduce
+	the mean squared displacements (MSDs) exhibited by the solutes in our MD
+	simulations. We then demonstrate how we can use realizations orders of
+	magnitude longer than our MD simulations in order to predict solute flux and
+	selectivity.  This is among the first studies to apply time series modeling
+	approaches in order to predict macroscopic transport properties from molecular
+	dynamics trajectories.
 
@@
 
-	%BJC: included phone numbers because it asked to do so in author's guide.
 	\noindent Some suggestions for reviewers are:
@@
 			with applications to soft materials. (University of
-			Potsdam, \href{mailto:kakania@uni-potsdam.de}{kakania @
-			uni-potsdam.de})
+			Potsdam, \href{mailto:kakania@uni-potsdam.de}{kakania@uni-potsdam.de})
 
@@
 			transport processes in polymeric nanofiltration and
-			reverse osmosis membranes. (Northwestern University
+			reverse osmosis membranes. (Northwestern University,
 			\href{mailto:r-lueptow@northwestern.edu}{r-lueptow@northwestern.edu})

### 2020-02-07 Ben_Manuscripts/hdphmm/Outline.tex
HDP-HMM outline

@@
 
-%MRS: better to have the first outline shorter to iterate more quickly!
-%BJC1: right, this one has been in the works for a while now. Wrote the anomalous diffusion methods a long time ago
+%Predicting Flux and Selectivity of Solutes in a Nanostructured Membrane using the Infinite Hidden Markov Model
+\title{Stochastic Models Parameterized by the Infinite Hidden Markov Model Can Predict Flux and Selectivity of Solutes in Nanostructured Membranes.}
 
-%MRS: better to have a title that described a finding, rather than the
-%approach used.  But we may need to wait a bit further until we can decide on a finding.
-%MRS: also 'stochastic modeling' is pretty vague.  should be more precise. 
-\title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
-%MRS: we should discuss whether Chris Calderon would be on this one.  I would guess no, but I don't know for sure. 
-%BJC1: Yea maybe Chris as an acknowledgement on this one. He didn't directly contribute anything other than pointing
-%me towards Greg Morrin who pointed me towards useful anomalous diffusion literature.
-\author{Benjamin J. Coscia \and Michael R. Shirts}
+\author{Benjamin J. Coscia, Chris Calderon \and Michael R. Shirts}
 
@@
   \section{Introduction}
-  %BJC: obviously this section will get beefed up
+
   We need highly selective membranes in order to perform efficient separations. \\
@@
   Lyotropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
-  into mechanically strong membranes.
-  \begin{itemize}
-  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
-	sized pores and have the potential to disrupt conventional membrane separation
-	techniques by being selective based not only on size and charge, but on chemical
-	functionality as well.
-	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
-	pores. They are easier to make.
-  \end{itemize}
+  into mechanically strong membranes.\\
+%  \begin{itemize}
+%  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
+%	sized pores and have the potential to disrupt conventional membrane separation
+%	techniques by being selective based not only on size and charge, but on chemical
+%	functionality as well.
+%	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
+%	pores. They are easier to make.
+%  \end{itemize}
 
@@
   solute-specific separations.\\
-
-  \noindent In our previous work, we studied the transport of 20 small polar molecules
-  in an H\textsubscript{II} phase LLC membrane.
-  \begin{itemize}
-    \item In general, we observed subdiffusive transport behavior characterized by 
-    intermittent hops separated by periods of entrapment.
-    \item We identified three mechanisms responsible for the solute trapping behavior:
-    entanglement among monomer tails, hydrogen bonding with monomer head groups, and
-    association with sodium counter ions.
-  \end{itemize}
 
@@
   	\item Brief description of anomalous diffusion
-  	\item Brief descritpion of MSDDM
+  	\item Brief description of MSDDM
   \end{itemize}
@@
   % The former is definitely simpler.
-  In this work, we apply the infinite hidden markov model, a modeling that is agnostic
-  to the source of time series data, in order to detect and parameter an unknown number
-  of autoregressive modes.
+  In this work, we apply the infinite hidden markov model (iHMM), a modeling
+  approach that is agnostic to the source of time series data, in order to 
+  automatically detect and infer the parameters of an unknown number of latent
+  autoregressive modes. \\
+
+  We study the same four solutes from our previous work. \\
+
+  We use the iHMM to generate stochastic trajectory realizations that share the same
+  dynamical characteristics as solute trajectories observed in our MD simulations. 
+  \begin{itemize}
+    \item The trajectories are qualitatively similar, showing expected hopping and trapping
+    behavior
+    \item They are quantitatively similar in that they reproduce the MSDs measured in MD
+  \end{itemize}
+
+  Finally, we use the stochastic trajectory realizations in order to compute the MFPT 
+  of solutes in macroscopic length pores.
+  \begin{itemize}
+  	\item We relate the MFPT to flux and compare the fluxes between solutes to get selectivity.
+  \end{itemize}
 
@@
 
-  We ran all MD simulations and energy minimizations using GROMACS 2018. We  % needs gromacs citations
+  We ran all MD simulations and energy minimizations using GROMACS 2018. We
   performed all post-simulation trajectory using python scripts which are available
-  %MRS: eventually want to say what scripts were used to do what, but that is not at the outline stage!
-  %BJC1: I usually put a table like that in the SI. Is that sufficient?
   online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
@@
   \subsection{Molecular Dynamics Simulations}
+
+  % BJC: Could I just reference previous work here? "MD simulations were run as 
+  % described in our previous work..."
 
@@
     \item Appropriate stochastic modeling requires that solutes sample the 
-    accessible mechanisms with representative probability.  %BJC1: incorporated suggested phrasing
+    accessible mechanisms with representative probability.
   \end{itemize}
@@
     have a relatively diverse set of chemical functionality.   
-    %MRS: do the solutes also have some diversity of mechanisms (that were observed previously?)
-    %BJC1: Yes. Need to put following into words
-    %BJC1: Ranking of time spent in pore region: AcOH > EG > URE > MeOH  (spans 4th most to 3rd least)
-    %BJC1: All have high hop frequency which is consistent with fast motion
-    %BJC1: Hbonding: Urea barely hbonds. AcOH and EG hbond a lot. AcOH has highest hbond lifetime of all 20 solutes. MeOH on par with all other simple alcohols
-    %BJC1: Sodium Association: Urea coordinates with sodium the most of all 20 solutes. AcOH, EG, MeOH spread out of rest of range. Lifetime similar 
     \item For each solute we created a separate system and to each system we
@@
 
-  % BJC: can ignore this section for now. 
-  \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}  %BJC: potentially a separate paper
+  \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}
+  %BJC: There is a fair amount of detail here just so I could understand better by writing it out
 
@@
   for modeling sequences of observations where the probability of the next observation
-  in a sequence depends only on a previous unobserved, or hidden, state.~\cite{beal_infinite_2002}
+  in a sequence depends only on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
   \begin{itemize}
@@
     \item One can partially overcome this by testing a range of numbers of 
-    hidden states and determining which is the best representation of their
+    hidden states and determining which is the best representation of the
     data.
@@
 
+  %BJC: I'm not sure how much of this I should include. This is pretty much 
+  % a reproduction of Fox et al's explanation: https://ieeexplore.ieee.org/abstract/document/5563110
   The infinite-state HMM overcomes this drawback by placing a hierarchical
@@
 
+  %BJC: I do need to include this
   \noindent We describe the dynamics of each state using a vector autoregressive (VAR) model. 
   \begin{itemize}
-  	\item A VAR process is characterized by a vector of observations in a time series 
-  	that are dependent on $r$ previous values of the time series vector, weighted by a
-  	coefficient matrix $A_i$ in addition to a white noise term $\mathbf{e}_t$:
+  	\item A VAR($r$) process is characterized by a vector of observations in a time series 
+  	that are linearly dependent on $r$ previous values of the time series vector:
   	\begin{equation}
-  	\mathbf{y}_t = \sum_{i=1}^r A_i\mathbf{y}_{t-i} + \mathbf{e}_t~~~~\mathbf{e}_t \sim N(0, \Sigma)
+  	\mathbf{y}_t = \mathbf{c} + \sum_{i=1}^r A_i\mathbf{y}_{t-i} + \mathbf{e}_t~~~~\mathbf{e}_t \sim N(0, \Sigma)
   	\end{equation}
-  	\item We assumed multivariate Gaussian noise and limited our analysis to an 
-  	autoregressive order of $r=1$.
+  	Previous observations are weighted by coefficient matrices $A_i$. The VAR($r$) 
+  	process is further characterized by a shift in the mean of each dimension by the
+  	vector $\mathbf{c}$ and a white noise term $\mathbf{e}_t$.~\cite{hamilton_time_1994}
+  	\item We assumed multivariate Gaussian noise, with mean zero and covariance, $\Sigma$.
+  	\item We limited our analysis to an autoregressive order of $r=1$. %BJC: might try higher orders, but probably not worth it
   	\item We used a conjugate matrix-normal inverse-Wishart prior on parameters
-  	$A$ and $\Sigma$ in order to analytically draw from the posterior.
+  	$A$ and $\Sigma$ and a conjugate Gaussian prior on $\mathbf{c}$ in order to analytically
+  	draw from the posterior.~\cite{fox_nonparametric_2009}
   \end{itemize}
 
-  Based on the VAR parameters and matrix of transition probabilities, we calculated
-  the most likely sequence of hidden states.
+  %Based on the algorithms developed by Fox et al.~\cite{fox_sticky_2007}, 
+  Using the iHMM framework, we estimated the most likely number and sequence of hidden states
+  while simultaneously estimating VAR(1) parameters for each state and the overall 
+  state transition probability matrix, $T$.
   \begin{itemize}
-    \item We repeated this process iteratively until we reached convergence % BJC: need to define convergence criteria
-    \item Our python implementation of this process is heavily adapted from the MATLAB code
-    of Fox et al.~\cite{fox_sticky_2007} 
+    \item We created a python implementation of this process which we heavily adapted from
+    the MATLAB code of Fox et al.~\cite{fox_sticky_2007} 
+    \item Parameter estimation is iterative. Therefore, we looked for convergence 
+    as shown in SI.
     \item We refer the interested reader to much more extensive descriptions of 
@@
   \end{itemize}
-  \break
+
+  We generated stochastic realizations by drawing state sequences based on the
+  rows of $T$. 
+  %BJC: lots more implementation details once that is ironed out
+
+  \subsection{Estimating Flux and Selectivity}
+  %BJC: can make this discussion somewhat short since it's already in previous paper. 
+  % Should probably just hit all the main equations quickly.
+
+  \noindent We calculate first passage times by propagating stochastic trajectories until they
+  reach distance $L$. \\
+
+  We determine the mean first passage time (MFPT) using the following equation:~\cite{cussler_diffusion:_2009}
+  \begin{equation}
+  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
+  \label{eqn:passage_times}
+  \end{equation}
+
+  \noindent Flux, $J$, is simply 1 / MFPT by the Hill relation.~\cite{hill_free_1989} \\
+
+  In our previous work, we showed that, in the absence of convective solute flux, selectivity
+  towards solute $i$ versus solute $j$ can be calculated by:  
+  \begin{equation}
+  S_{ij} = \frac{J_i / \Delta C_i}{J_j / \Delta C_j}
+  \label{eqn:selectivity}
+  \end{equation}
+  where $\Delta C_j$ is the trans-membrane concentration difference.
+
   \section{Results and Discussion}
+
+  \noindent Trajectory realizations qualitatively match MD simulation trajectories.
+  \begin{itemize}
+    \item Look for hopping and trapping behavior
+  \end{itemize}
+
+  \noindent MSDs generated from stochastic trajectories match those from MD.
+  \begin{itemize}
+  	\item Look at curvature and 1-$\sigma$ confidence intervals
+  \end{itemize}
+
+  \noindent We can relate the identified states back to transport mechanisms.
+  \begin{itemize}
+  	\item More detailed discussion of identified states
+  	\item How size of fluctuations, autoregressive parameters are influenced by trapping mechanisms
+  	\item Any new states?
+  \end{itemize}
+
+  \noindent We can predict macroscopic flux and selectivity.
+  \begin{itemize}
+  	\item Flux as function of pore length
+  	\item Selectivity as function of pore length (if flux scaling is length-dependent)
+  \end{itemize}
 
@@
 
-  We have tested two different mathematical frameworks for describing solute
-  motion in an H\textsubscript{II} phase LLC membrane.
-  \begin{itemize}
-    \item Markov state modeling with predefined states gives a nice description
-    of transitions between observed states as well as the type of stochastic 
-    behavior shown in each state. However, it doesn't accurately portray correlated
-    time series behavior leading to overpredicted MSDs.
-    \item Subordinated fractional Brownian motion has a nice theoretical foundation
-    in the anomalous diffusion literature. A two mode model that describes dynamics
-    based on whether a solute is in or out of the pore region leads to MSDs fairly
-    consistent with MD simulated trajectories.
-  \end{itemize}
+  \noindent We have shown that the iHMM can be used to parameterize solute time series
+  with an unknown number of latent dynamical modes. \\
+
+  \noindent We can use the iHMM to help identify mechanisms by relating the latent
+  states to observed solute behavior. \\
+
+  \noindent We can use the iHMM to predict macroscopic transport properties. \\
+
+  \noindent The iHMM is not limited to the H\textsubscript{II} phase.
 
@@
   \bibliographystyle{ieeetr}
-  \bibliography{stochastic_transport}
+  \bibliography{hdphmm}
 

### 2020-02-07 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
HDP-HMM outline

@@
   Next, we generalize Markov state models, treating the
-  configurational state of the system as a Markov process, each
-  state of which has  
-  %MRS10:
-  %each having separate
-  distinct transport properties. For each state and transition
+  configurational states of the system as a Markov process where each
+  state has distinct transport properties. For each state and transition
   between states, we parameterize the distribution and temporal correlation 
@@
   decrease a Q\textsubscript{I} phase membrane's permeability relative to the
-  H\textsubscript{II} phase, it is considerably easier to 
-  %MRS10: synthesis implies chemical synthesis, this is really assembly - but produce is more general. 
-  %synthesize 
-  produce 
+  H\textsubscript{II} phase, it is considerably easier to produce 
   at scale.~\cite{hatakeyama_nanoporous_2010}
@@
   Using a bottom-up modeling approach, we can parameterize single particle
-  behavior by extracting 
-  %MRS10: their is referring to behavior, which is singular - changing grammar.
-  %their 
-  particle
-  trajectories from MD simulations and studying
+  behavior by extracting particle trajectories from MD simulations and studying
   the properties that have the greatest influence on solute dynamics. With this
@@
   uncertainties. Fortunately, there is an abundance of information encoded in
-  the complex solute trajectories. 
-  %MRS: moving clause out from top.
-  %Into a model, 
-  We can incorporate fluctuations and
-  time-dependent correlations in solute position 
-  %MRS added:
-  into transport models, 
-  as well as the length of time
-  solutes are trapped. We can add further detail by integrating
+  the complex solute trajectories. We can incorporate fluctuations and 
+  time-dependent correlations in solute position into transport models, 
+  as well as the length of time solutes are trapped. We can add further detail by integrating
   this time series analysis with our knowledge of the primary trapping
@@
 
-  We constructed our first model by applying the 
-  %MRS10: tweaked
-  existing
-  rigorous theoretical
-  foundation 
-  %already developed 
-  to describe the motion of 
-  particles 
-  %MRS10: added specificity
-  simulated at the atomistic level
-  %exhibiting
-  which exhibit
-  non-Brownian, or anomalous, transport
-  behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
+  We constructed our first model by applying the existing rigorous theoretical
+  foundation which describes the motion of particles that exhibit non-Brownian,
+  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
   introduced by fractional calculus are instrumental to this
@@
   radial distance from the closest pore center. This allows us to include
-  different dynamical behavior of solutes 
-  %MRS10: added, to show that this is informed by looking at the trajectories.
-  previously
-  observed within the pore region
-  versus within the monomer tails.
-
-  %MRS10: tweaked, also made plural since multiple models are built.
-  %Where applicable, the sFBM model 
+  the different dynamical behavior of solutes previously observed within the
+  pore region versus within the monomer tails.
+
   Where sufficiently close to observed data, these fitted sFBM models
-  provides a way to propagate information
-  about solute trajectories gathered at the microsecond time scale to realistic
-  experimental time scales. They can also confirm the importance of assumed
-  solute-membrane interactions used to define the model's functional form, and
+  provide a way to propagate information about solute trajectories gathered 
+  at the microsecond time scale to realistic experimental time scales. 
+  They can also confirm the importance of assumed solute-membrane interactions 
+  used to define the model's functional form, and
   suggest missing components. They can help researchers formulate hypotheses to
@@
   work: methanol, urea, ethylene glycol and acetic acid. In addition to moving
-  %MRS10: tweaked, may not be quick in absolute terms.
-  more 
-  quickly
-  than other solutes studied previously, 
-  allowing them to extensively explore membrane structural space,
-  these solutes have a range of chemical functionality and experience each of
-  the three trapping mechanisms to different extents.
+  more quickly than other solutes studied previously, allowing them to extensively
+  explore membrane structural space, these solutes have a range of chemical 
+  functionality and experience each of the three trapping mechanisms to different extents.
 
@@
   to a discrete power law distribution whose maximum likelihood $\alpha$ 
-  parameter we calculated by maximizing the 
-  %MRS10: added for precision
-  log
-  likelihood function: 
+  parameter we calculated by maximizing the log likelihood function: 
   \begin{equation}
@@
   to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model.
-  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the 
-  %MRS10:
-  log 
+  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the log 
   likelihood function:~\cite{clauset_power-law_2009}
@@
 
-  %BJC3: not sure how to cite fbm
-  %TODO: cite github page for fbm
-  We used the Python package \texttt{fbm} to generate exact simulations of FBM
-  %MRS10: add a reference to where your implementation can be found.
-  and our own Python implementation of the algorithm by Stoev and Taqqu to
+  We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
+  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
+  the Supplemental Material) of the algorithm by Stoev and Taqqu to
   simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
@@
   states with transitions between states defined by a transition probability
-  matrix, $T$.  
-  %MRS10: split sentence for readability.
-  $T$ describes the conditional probability of moving to a
+  matrix, $T$.  $T$ describes the conditional probability of moving to a
   specific state given the previously observed
@@
   get the MFPT.
-  %MRS8: check to make sure there is goodness-of-fit checks in the SI for fitting to the analytical model.
-  %BJC8: TODO
 
@@
   \end{subfigure}
-  \caption{
-    %MRS10: added
-    Three
-    representative trajectories generated from each solute exhibit hops
+  \caption{Three representative trajectories generated from each solute exhibit hops
 	  between periods of entrapment, characteristic of a CTRW. Solute
@@
   \caption{Using urea as an example, (a) the distribution of hop lengths can be
-	  fit by a Gaussian 
-          ``as well as'' is ambiguous, can mean ``in addition to'' or ``similar in quality to''
-          %as well as 
-          almost as well as
-          a more general L\'evy stable
+	  fit by a Gaussian in addition to a more general L\'evy stable
 	  distribution, though the L\'evy stable distribution does a better job of
@@
   Urea and acetic acid appear to demonstrate satisfactory stationarity. The
-  shapes of 
-  %MRS10: which of the solutes does ``their'' refer to?  Be more explicit.
-  their MSD curves are also very similar (see
+  shapes of urea and acetic acid's MSD curves are also very similar (see
   Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).
@@
   parameterize AD models with all available data after the perceived
-  equilibration time. The MSD curves generated from 
-  %MRS10: added
-  both 
-  %MRS10: more grammatically correct to say ``one and two'' instead of ``1 and 2''
-  the one and two mode models
-  are overlayed with the MD simulated MSDs for comparison in
+  equilibration time. The MSD curves generated from both the one and 
+  two mode models are overlayed with the MD simulated MSDs for comparison in
   Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
@@
 	  autocorrelation function, $\gamma(H)$, to describe the degree of
-	  correlation between hops. 
-          %MRS10: tweaked
-          Simulations with higher values of $H$ display behavior closer to
-	  the Brownian limit.}\label{fig:1mode_parameters}
+	  correlation between hops. Simulations with higher values of $H$ display
+	  behavior closer to the Brownian limit.}\label{fig:1mode_parameters}
   \end{figure}
@@
   to match the curvature of MD quite well, but closer examination reveals that
-  the MD MSD curve 
-  %MRS10: being a bit more cautious about claims.
-  %actually shifts 
-  may actually shift
-  from a sub-linear to a linear regime around
+  the MD MSD curve may actually shift from a sub-linear to a linear regime around
   500 ns.
@@
 
-  %MRS10: tweak
-  %Turning first to 
-  Examining first
-  the parameters of the one mode model, we can begin to break
+  Examining first the parameters of the one mode model, we can begin to break
   down the trends in solute MSDs. The parameters belonging to ethylene glycol
   and methanol are relatively similar, which is consistent with their similar MD
-  MSDs
-  %MRS10: added
-  and qualitatively similar MD timeseries.
+  MSDs and qualitatively similar MD timeseries.
   Relative to ethylene glycol, methanol tends to stay trapped for less
@@
   region where collisions with tails are frequent.
-% BJC: made more to the point
-%  In fact, methanol has the lowest
-%  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
-%  it appears that our model under-predicts the methanol MSD curve relative
-%  to other solutes. However, it remains plausible that methanol does have a low $H$ 
-%  value because it spends the majority of its time outside the pore region where collisions
-%  with tails are frequent. 
   Urea has the third highest MSD which is primarily a consequence of more
@@
   To create an MSDDM for each solute, we determined the state sequence associated
-  with each solute trajectory 
-  %MRS10: added for clarity to make sure people who how the state sequence was determined.
-  based on the geometric indicators of the states indicated in Table~\ref{table:states}.
-  and then generated emission distributions of fluctuations
+  with each solute trajectory based on the geometric indicators of the states 
+  indicated in Table~\ref{table:states}. We then generated emission distributions of fluctuations
   within each state as well as transitions between states. In theory, one could 
@@
   pronounced than that seen in the hop length distributions of the previous
-  section.  
-  %MRS10: break for clarity.
-  We therefore did not consider the Gaussian case (see
+  section. We therefore did not consider the Gaussian case (see
   Figure~\ref{fig:gaussian_levy_comparison}). The correlation structure
@@
   \end{subfigure}
-  %MRS10: Probably will need to make the font labels bigger in a revision.
   \caption{The parameters of the MSDDM are strong functions of trapping
@@
 	  influencing trapping mechanisms increases, the Hurst parameter, $H$,
-	  decreases. $H$ is 
-          highest 
-          %MRS10
-          (closest to Brownian)
-          during transitions between states (state
-	  T). (b) As more trapping mechanisms simultaneously influence solutes,
+	  decreases. $H$ is highest (closest to Brownian) during transitions 
+	  between states (state T). (b) As more trapping mechanisms simultaneously influence solutes,
 	  the width of the hop length distribution ($\sigma$) decreases. The
@@
 
-  %MRS10: is it a good idea to say they are well-captured when we get results qualitatively different from MD later?
-  The dynamics of urea, ethylene glycol and, to a lesser extent, methanol appear
-  to be well-captured by the MSDDM. We simulated 1000 MSDDM trajectory realizations
+  Quantitatively, the dynamics of urea, ethylene glycol and, to a lesser extent, 
+  methanol appear to be well-captured by the MSDDM. We simulated 1000 MSDDM trajectory realizations
   for each solute, as described in Section~\ref{method:MSMs}, then calculated their
@@
 	  (black). The trajectories are qualitatively similar to what one
-	  might expect for Brownian motion
-          %MRS10: added for context
-          even though the MSDs are often similar to the atomistic systems.
+	  might expect for Brownian motion even though the MSDs are often similar
+	  to the atomistic systems.
   	  }\label{fig:msddm_eyetest}
@@
   H\textsubscript{II} LLC membrane synthesized with the monomer in this work
-  was 7$\mu$m thick. 
-  %MRS10: provide citation here for the fact of 7mum thick.
+  was 7$\mu$m thick.~\cite{feng_thin_2016}
   Using 24 cores to simulate trajectory realizations in
@@
   solute behavior. Even if our model is not perfect, it provides clear logic
-  behind the mechanisms leading to selective behavior 
-  %MRS10: softened claim a bit - it hasn't been used for design yet.
-  %which is very important for design. 
-  which could significantly help illuminate any design choices.
-  We hope this type of analysis can be leveraged to explore new,
-  interesting and complex separations problems.
+  behind the mechanisms leading to selective behavior which could significantly
+  help illuminate any design choices. We hope this type of analysis can be 
+  leveraged to explore new, interesting and complex separations problems.
 
@@
   lengths and dwell times. 
-  %MRS10: may want to mention a bit about the weakness of the methods (i.e. say something about what 
-  % can be done even given the lack of correlation structure), since it's in the conclusion.
   The MSDDM is a powerful way to characterize explicit
@@
   re-designs an LLC monomer to eliminate one source of trapping, then 
-  %MRS10: tweaked 
-  %high
-  higher
-  selectivities 
-  may result.
-  %are possible. 
-  %Our 
-  The modeling approaches presented in this paper 
-  facilitate new ways of approaching
-  complex separation problems.
+  higher selectivities may result. The modeling approaches presented in this paper 
+  facilitate new ways of approaching complex separation problems.
 

### 2020-02-07 Ben_Manuscripts/stochastic_transport/cover_letter.tex
HDP-HMM outline

--- 2020-01-21 Ben_Manuscripts/stochastic_transport/cover_letter.tex
@@
 	our MD simulations. We explore two modeling approaches. First, based on the
-	anomalous diffusion literature, we hypothesize that solutes are subject 
-	to subordinated fractional Brownian or L\'evy motion. This implies that 
+	anomalous diffusion literature, we parameterize solute motion as 
+    subordinated fractional Brownian and L\'evy motion processes. This implies that 
 	solutes experience a series of dwell times separated by anti-correlated hop
@@
 	between various trapped states, each with different dynamical properties.
-
-%        Recently, we characterized an atomistic molecular model of an
-%        LLC membrane that is maximally consistent with experimental
-%        observations (Coscia et al. \textit{J. Phys. Chem. B}, 123,
-%        289--309 (2019)). In this work, we observe and quantify
-%        transport of water, sodium and 20 small polar solutes within
-%        the pores of our atomistic H\textsubscript{II} phase LLC
-%        membrane model. In general, all solutes exhibit subdiffusive
-%        transport behavior characterized by intermittent hops between
-%        long periods of entrapment. However, due the pores'
-%        inhomogeneous architecture, we observed 3 different mechanisms
-%        of entrapment. First, solutes can diffuse out of the pores and
-%        become entangled between tails. Second, many of the solutes
-%        are capable of donating hydrogen bonds to monomer head groups
-%        for extended periods of time. Finally, solutes can associate
-%        with monomer head group counter-ions within nanopores. Each
-%        solute is influenced by each mechanism to varying degrees
-%        dependent on its size and chemical functionality. We begin our
-%        discussion with a broad description of these mechanisms in the
-%        context of all solutes before restricting the discussion to
-%        more detailed analyses of subsets of chemically-similar
-%        solutes.
+	Finally, we demonstrate how one can project our best model onto macroscopic 
+	timescales in order to estimate solute flux and selectivity.
 

### 2020-02-12 Ben_Manuscripts/thesis/intro.tex
starting dissertation

\chapter{Introduction}\label{chapter:intro}

  \section{Industrial Need for Highly Selective Separations}

  \subsection{Desalination}

  \subsection{Separation of Organic Micropollutants}

  \subsection{Recovery of Valuable Dissolved Species}

  \subsection{Breathable Barriers}

  \section{Cross-linked Self Assembled Liquid Crystal Membranes for Selective Aqueous Separations}

  \subsection{The H\textsubscript{II} Phase}

  \subsection{The Q\textsubscript{I} Phase}

  \section{Atomistic Molecular Simulation of LLC Membranes}

### 2020-02-12 Ben_Manuscripts/thesis/structure.tex
starting dissertation

--- 2018-11-21 Ben_Manuscripts/structure_paper/Final_Draft.tex
@@
-\documentclass[journal=jpcbfk,manuscript=article]{achemso}
-
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{amsmath} 
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{xr}
-
-\SectionNumbersOn
-
-\externaldocument[S-]{supporting_information}
-
-\title{Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
-\author{Benjamin J. Coscia}
-\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
-\author{Joseph Yelk}
-\author{Matthew A. Glaser}
-\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
-\author{Douglas L. Gin}
-\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
-\alsoaffiliation{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
-\author{Xunda Feng}
-\affiliation{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
-\author{Michael R. Shirts}
-\email{michael.shirts@colorado.edu}
-\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
-\begin{document}
-
-  \graphicspath{{./figures/}}
-
-  \begin{abstract}
-
-  %NOTE: all deleted comments are still in Draft.tex
-
-  Periodic, nanostructured porous polymer membranes made from the cross-linked
-  inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
-  a promising class of materials for selective separations. In this work, we
-  investigate an experimentally characterized LLC polymer membrane using
-  atomistic molecular modeling. In particular, we compare simulated X-ray
-  diffraction (XRD) patterns with experimental XRD data to quantify and
-  understand the differences between simulation and experiment.  We find that the
-  nanopores are likely composed of 5 columns of stacked LLC monomers which
-  surround each hydrophilic core. Evidence suggests that these columns likely
-  move independently of each other over longer time scales than accessible via
-  atomistic simulation. We also find that WAXS structural features previously
-  attributed to monomer tail tilt is likely instead due to ordered tail packing.
-  Although this system has been reported as dry, we show that small amounts of
-  water are necessary to reproduce all features from the experimental XRD pattern
-  due to asymmetries introduced by hydrogen bonds between the monomer head groups
-  and water molecules. Finally, we explore the composition and structure of the
-  nanopores and reveal that there exists a composition gradient rather than an
-  abrupt partition between the hydrophilic and hydrophobic regions. A caveat is
-  that the time scales of the dynamics are extremely long for this system,
-  resulting in simulated structures that appear too ordered, thus requiring
-  careful examination of the metastable states observed in order to draw any
-  conclusions. The clearer picture of the nanoscopic structure of these membranes
-  provided in this study will enable a better understanding of the mechanisms of
-  small molecule transport within these nanopores.
-
-  \end{abstract}
+\chapter{Understanding Nanoscale Membrane Structure}\label{chapter:structure}
 
@@
 SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
-		from Ref.\citenum{feng_thin_2016}) The repeat spacing in the 1D-SAXS
-		scattering pattern is characteristic of hexagonal packing. The leading peak,
-		q*, represents the distance between the d\textsubscript{100} planes, which translates 
-                into a distance between pore centers of 4.12 nm.} 
+from Ref.\cite{feng_thin_2016}) The repeat spacing in the 1D-SAXS scattering
+pattern is characteristic of hexagonal packing. The leading peak, q*,
+represents the distance between the d\textsubscript{100} planes, which
+translates into a distance between pore centers of 4.12 nm.} 
 	\label{fig:SWAXS}
@@
   \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Additional details are available in 
-  Section \ref{S-section:python_scripts} of the Supporting Information (SI).
+  Section \ref{S-section:python_scripts_structure} of the Supporting Information (SI).
 
@@
   \end{subfigure}
-  \caption{(a) We measured the intensity of R-alkanes by calculating the average 
-  intensity within the region bounded by $|\mathbf{q}|$ = 1.4~$\AA^{-1}$ and 
-  1.57~$\AA^{-1}$ (between 4.0 and 4.5 \AA~in real space). We excluded intensities
-  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
-  simulated spectra overlap with R-$\pi$ in those regions in all cases. (b) We
-  measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
-  cross-section of the diffraction pattern. (c) We measured the intensity of R-spots
-  by averaging the peak heights produced by radially integrating the patterns within 
-  the R-alkanes region. We took the intensity of R-spots as the average of the 
-  peak intensities near 37 and 143$\degree$. (d) We measured the intensity of 
-  R-pores by measuring the height of the d\textsubscript{100} peak (the leading
-  peak closest to $q_r$=0) of the cross-section of the diffraction patterns along
-  the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
+  \caption{(a) We measured the intensity of R-alkanes by calculating the
+average intensity within the region bounded by $|\mathbf{q}|$ = 1.4~\AA$^{-1}$
+and 1.57~\AA$^{-1}$ (between 4.0 and 4.5 \AA~in real space). We excluded
+intensities within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$,
+since the simulated spectra overlap with R-$\pi$ in those regions in all cases.
+(b) We measured the intensity of R-$\pi$ and R-double based on the peaks of the
+$q_z$ cross-section of the diffraction pattern. (c) We measured the intensity
+of R-spots by averaging the peak heights produced by radially integrating the
+patterns within the R-alkanes region. We took the intensity of R-spots as the
+average of the peak intensities near 37 and 143$\degree$. (d) We measured the
+intensity of R-pores by measuring the height of the d\textsubscript{100} peak
+(the leading peak closest to $q_r$=0) of the cross-section of the diffraction
+patterns along the $q_r$ axis at $q_z$=0.
+  } \label{fig:xrd_intensities}
   \end{figure}
@@
 
-  \subsubsection{\textit{Radial Distribution Functions}}\label{method:rdfs}
+  \subsubsection{\textit{Radial Distribution Functions}}\label{method:radial_distribution_functions}
 
@@
   \begin{tabular}{cccc}
-  \toprule
+  \hline
   System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
-  \midrule
+  \hline
   Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
@@
   Experiment         & --                 &    3.70                    & 9 $\pm$ 1               \\
-  \bottomrule
+  \hline
   \end{tabular}
@@
   \begin{tabular}{c|ccccc}
-  \toprule
+  \hline
  		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
@@
   Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
-  \midrule
+  \hline
   R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
@@
   \hline
-   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
+   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~$\AA$^{-1}$)}     \\
   \hline
@@
   Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
-  \midrule
+  \hline
   R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
@@
   R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
-  \bottomrule
+  \hline
   \end{tabular}
@@
   \includegraphics[width=\textwidth]{exp_rsection_fit.pdf}
-  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
+  \caption{FWHM = 0.792 $\pm$ 0.009 \AA$^{-1}$}\label{fig:exp_rsection_fit}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{sim_rsection_fit.pdf}
-  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
+  \caption{FWHM = 0.796 $\pm$ 0.011 \AA$^{-1}$}\label{fig:sim_rsection_fit}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{exp_zsection_fit.pdf}
-  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
+  \caption{FWHM = 0.110 $\pm$ 0.003 \AA$^{-1}$}\label{fig:exp_zsection_fit}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{sim_zsection_fit.pdf}
-  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
+  \caption{FWHM = 0.163 $\pm$ 0.011 \AA$^{-1}$}\label{fig:sim_zsection_fit}
   \end{subfigure}
@@
 
-  \subsubsection*{Distance and Correlation Between Stacked Monomer Head Groups}
+  \subsubsection{Distance and Correlation Between Stacked Monomer Head Groups}
 
@@
 
-  \subsubsection*{Shape and Intensity of the $q_r$ Cross-section of R-$\pi$}\label{section:rpi_xsection}
+  \subsubsection{Shape and Intensity of the $q_r$ Cross-section of R-$\pi$}\label{section:rpi_xsection}
 
@@
   especially problematic when comparing the FWHM of the $q_z$ cross-section of
-  R-$\pi$, where the experimental FWHM (0.11 $\AA^{-1}$) is similar to the bin
-  size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).  Additionally, we model each
+  R-$\pi$, where the experimental FWHM (0.11 \AA$^{-1}$) is similar to the bin
+  size in the $q_z$ direction (ca. 0.07 \AA$^{-1}$).  Additionally, we model each
   atom with a Gaussian sphere of electron density, which is a simplification.
@@
   \begin{tabular}{c|ccc|ccc}
-  \toprule
+  \hline
    		                        &           \multicolumn{3}{c}{Thermal Disorder}             &             \multicolumn{3}{c}{Quenched Disorder}               \\
-  \midrule
-  System                        & $\sigma_x$ ($\AA$) & $\sigma_y$ (rad) & $\sigma_z$ ($\AA$) & $\sigma_z$ ($\AA$) & $\sigma_\theta$ (rad) & $\sigma_r$ ($\AA$) \\
-  \midrule
+  \hline
+  System                        & $\sigma_x$ (\AA) & $\sigma_y$ (rad) & $\sigma_z$ (\AA) & $\sigma_z$ (\AA) & $\sigma_\theta$ (rad) & $\sigma_r$ (\AA) \\
+  \hline
   Ordered Sandwiched            &         0.31       &       0.33       &        0.34        &        1.48        &     0.43              &     2.30           \\
@@
   Disordered Parallel Displaced &         0.39       &       0.31       &        0.33        &        1.65        &     0.43              &     2.63           \\
-  \bottomrule
+  \hline
   \end{tabular}
@@
 
-  \subsubsection*{Quenched Disorder in Ensembles of Configurations}
+  \subsubsection{Quenched Disorder in Ensembles of Configurations}
 
@@
 
-  \subsubsection*{The Implications of the New-found Understanding of R-$\pi$}
+  \subsubsection{The Implications of the New-found Understanding of R-$\pi$}
 
@@
   together in the $z$-direction. Blue monomers were stacked above orange monomers in the
-  initial configuration.}\label{fig:hbonds}
+  initial configuration.}\label{fig:hydrogen_bonds}
   \end{figure}
@@
   existing system, as well as to evaluate new unsynthesized LLC systems.
-
-  \section*{Supporting Information}
-
-  Detailed explanations and expansions upon the results and procedures mentioned in 
-  the main text are described in the Supporting Information. This information is 
-  available free of charge via the Internet at http://pubs.acs.org.
-
-  \section*{Acknowledgements}
-
-  J. Y. and M. A. G. were supported by the Soft Materials Research Center under NSF 
-  MRSEC Grant DMR-1420736
-
-  Molecular simulations were performed using the Extreme Science and
-  Engineering Discovery Environment (XSEDE), which is supported by National
-  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
-  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
-  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
-  which is supported by the National Science Foundation (awards ACI-1532235 and
-  ACI-1532236), the University of Colorado Boulder, and Colorado State
-  University. The Summit supercomputer is a joint effort of the University of
-  Colorado Boulder and Colorado State University.
-
-  The authors thank Richard Noble, Michael McGrath, Gregory Dwulet and Sarah Dischinger
-  for useful discussions that enhanced our understanding of these LC membrane systems.
-
-  \clearpage
-  \bibliography{llc}
-
-  \newpage
-
-  \section*{TOC Graphic}
-  \begin{figure}
-  \includegraphics[width=3.25in]{new_toc_graphic.pdf}
-%  \includegraphics[width=4.5cm]{toc_image_final.pdf}
-%  \includegraphics[width=4.07cm]{toc_waxs.pdf}
- \end{figure}
-
-\end{document}
-
-% LocalWords:  Nanostructured desalination biorefinement solute RO NF bruggen
-% LocalWords:  polydisperse diffusivity solutes BJC ultrafiltration nanometer
-% LocalWords:  ionizable pretreatment Graphene solvated Na GA zhou resel feng
-% LocalWords:  ca wt mesophases al crosslinking THF nanoporous PDMS nanopores
-% LocalWords:  TODO svg eps atomistically counterion nanoscopic counterions XRD
-% LocalWords:  WAXS headgroups initio metastable timescales acessible leached
-% LocalWords:  SAXS alkane alkanes Antechamber bccsym molcharge QUACPAC Openeye
-% LocalWords:  Gromacs berendsen timescale Packmol xyz hydrophlic xy pd tshaped
-% LocalWords:  KJ NVT kJ Parrinello Rahman gmx solvate polymerization FRP FRPs
-% LocalWords:  crosslink binned DC MSD subharmonic matplotlib GAFF's xrd llc ab
-% LocalWords:  polarizable reconcilable screenshot crosslinked uncrosslinked AA
-% LocalWords:  nanofiltration permeability interfacial diamine polysulfone der
-% LocalWords:  trimesoyl immiscible polymerizes etching Osuji's nanostructured
-% LocalWords:  Donnan modelling nanotubes monodispersity maruyama Zeolites Col
-% LocalWords:  lyotropic thermotropic png kinetically colorbar gromacs hess dr
-% LocalWords:  gimp disassociate pore's barostat racemic colorbars Nernst LLCs
-% LocalWords:  entropic rzplot transitioning spoel github pymbar Yelk Glaser xr
-% LocalWords:  flowback FW wastewaters wastestream fracking semipermeable TFC
-% LocalWords:  solute's polymerized wijmans diffusivities amphiphilic MWCO Ia
-% LocalWords:  nanostructures bicontinuous hatakeyama tortuosity Pn hII TLC ing
-% LocalWords:  microstructures multilayer Xunda's refamiliarize nanostructure
-% LocalWords:  nanoscale TEM LC methacrylated Eq scipy equil xz meridional phys
-% LocalWords:  semiisotropic nocbar chem waxs ish fb entropically steric vv rpi
-% LocalWords:  highlimit yz nematically carboxylate norestraints rb Bushey cyan
-% LocalWords:  dihedrals cbar adenine carboxyl sterically QM hydroscopicity LCs
-% LocalWords:  nophenyls nowater hbonds notails decorrelated Decorrelating SI
-% LocalWords:  xlink uncross

### 2020-02-12 Ben_Manuscripts/thesis/structure_si.tex
starting dissertation

--- 2018-11-19 Ben_Manuscripts/structure_paper/supporting_information.tex
@@
-%\documentclass[journal=jpcbfk,manuscript=article]{achemso}
-\documentclass{article}
-
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{amsmath} 
-\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\usepackage{listings}
-\usepackage{xr}
-\usepackage{array}
-\usepackage{authblk}
-\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
-
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thesection}{S\arabic{section}}
-\renewcommand{\thepage}{S\arabic{page}}  
-\renewcommand{\thetable}{S\arabic{table}}
-
-%\SectionNumbersOn
-
-\externaldocument[M-]{Final_Draft}
-
-\title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
-\author[1]{Benjamin J. Coscia}
-\author[2]{Joseph Yelk}
-\author[2]{Matthew A. Glaser}
-\author[1,3]{Douglas L. Gin}
-\author[4]{Xunda Feng}
-\author[1]{Michael R. Shirts*}
-\date{E-mail: michael.shirts@colorado.edu}
-
-\affil[1]{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
-\affil[2]{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
-\affil[3]{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
-\affil[4]{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
-
-\begin{document}
-
-  \bibliographystyle{ieeetr}
-  %\graphicspath{{./figures/supporting_figures/}}  % put all the figures here
-  \graphicspath{{./figures/}}
-  \maketitle
-
-  \section{Setup and analysis scripts}\label{section:python_scripts}
+\chapter{Test}
+
+  \section{Setup and analysis scripts}\label{S-section:python_scripts_structure}
 
@@
   analysis, except for simulating X-ray diffraction (XRD) patterns, are available online at
-  \texttt{https://github.com/bencoscia/llcsim}. Table~\ref{table:python_scripts} provides more 
+  \texttt{https://github.com/bencoscia/llcsim}. Table~\ref{S-table:python_scripts_structure} provides more 
   detail about specific scripts used for each type of analysis performed in the main text.
@@
 
-  \section{Further details regarding monomer parameterization}\label{section:parameterization}
+  \section{Further details regarding monomer parameterization}\label{S-section:parameterization}
 
@@
 	last 10\% of the trajectory and was used to build all assemblies reported
-	(Figure~\ref{fig:monomer}).
+	(Figure~\ref{S-fig:monomer}).
 
@@
 		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
-		the blue atom is sodium.}\label{fig:monomer}
+		the blue atom is sodium.}\label{S-fig:monomer}
   \end{figure}
@@
   \hline
-  \texttt{/setup/param.sh} & \ref{M-method:parameterization} & Automatically run the monomer
-  parameterization scheme outlined in Section~\ref{section:parameterization} given an initial
+  \texttt{/setup/param.sh} & \ref{method:parameterization} & Automatically run the monomer
+  parameterization scheme outlined in Section~\ref{S-section:parameterization} given an initial
   structure file in .pdb format. \\ \hline
 
-  \texttt{/setup/build.py} & \ref{M-method:unitcell_build} \& \ref{M-method:monomer_placement} &
+  \texttt{/setup/build.py} & \ref{method:unitcell_build} \& \ref{method:monomer_placement} &
   Build an initial configuration in the sandwiched or parallel displaced configuration with the 
@@
 
-  \texttt{/setup/equil.sh} & \ref{M-section:equilibration} & Wrapper script for running the GROMACS 
+  \texttt{/setup/equil.sh} & \ref{section:equilibration} & Wrapper script for running the GROMACS 
   functions and python scripts needed in order to equilibrate an initial configuration. \\ \hline
 
-  \texttt{/analysis/Structure\_char.py} & \ref{M-method:pore_spacing} & Calculate the distance 
+  \texttt{/analysis/Structure\_char.py} & \ref{method:pore_spacing} & Calculate the distance 
   between pores. \\ \hline
 
-  \texttt{/analysis/correlation.py} & \ref{M-section:correlation_length} & Calculate the 3D 
+  \texttt{/analysis/correlation.py} & \ref{section:correlation_length} & Calculate the 3D 
   correlation function from a trajectory and plot desired slices. \\ \hline
 
-  \texttt{/analysis/regional\_density.py} & \ref{M-method:rdfs} & Calculate the density of a given
+  \texttt{/analysis/regional\_density.py} & \ref{method:rdfs} & Calculate the density of a given
   monomer component as a function of its distance from the pore center. \\ \hline
 
-  \texttt{/analysis/structure\_factor.py} & \ref{M-method:simple_systems} & Generate customizable
+  \texttt{/analysis/structure\_factor.py} & \ref{method:simple_systems} & Generate customizable
   trajectories of point scatterers, then calculate their structure factor and plot slices of it.
@@
 
-  \texttt{/analysis/disorder.py} & \ref{M-method:simple_systems} & Measure the magnitude of
+  \texttt{/analysis/disorder.py} & \ref{method:simple_systems} & Measure the magnitude of
   quenched disorder. \\ \hline
 
-  \texttt{/analysis/Ionic\_Conductivity.py} & \ref{M-method:ionic_conductivity} & Calculate the 
+  \texttt{/analysis/Ionic\_Conductivity.py} & \ref{method:ionic_conductivity} & Calculate the 
   ionic conductivity using the Nernst-Einsten relationship and collective diffusion model. \\ \hline
 
-  \texttt{/setup/xlink.py} & \ref{M-method:xlink} & Iteratively cross-link a system given an 
+  \texttt{/setup/xlink.py} & \ref{method:xlink} & Iteratively cross-link a system given an 
   initial configuration. \\ \hline
 
-  \texttt{/analysis/orientational\_order.py} & \ref{M-section:mon_per_pore} & Calculate the 
+  \texttt{/analysis/orientational\_order.py} & \ref{section:mon_per_pore} & Calculate the 
   nematic order parameter. \\ \hline
 
-  \texttt{/analysis/tilt.py} & \ref{M-section:rspots} & Calculate the angle between the xy plane
+  \texttt{/analysis/tilt.py} & \ref{section:rspots} & Calculate the angle between the xy plane
   and the vector extending from the front to the back of each monomer tail. \\ \hline
 
-  \texttt{/analysis/tail\_packing.py} & \ref{M-section:rspots} & Calculate the distribution of
+  \texttt{/analysis/tail\_packing.py} & \ref{section:rspots} & Calculate the distribution of
   angles between the center of mass of each monomer tail and its nearest neighbor monomer tails.
@@
 
-  \texttt{/analysis/hexagonal\_packing.py} & \ref{M-section:rspots} & Calculate Fourier transform of
-  2D array of hexagonal scatterers as shown in Figure~\ref{M-fig:hexagonal_ft} of the main text. \\ \hline
-
-  \texttt{/analysis/compare\_disorder.py} & \ref{M-section:rpi} & Measure quenched disorder for
+  \texttt{/analysis/hexagonal\_packing.py} & \ref{section:rspots} & Calculate Fourier transform of
+  2D array of hexagonal scatterers as shown in Figure~\ref{fig:hexagonal_ft} of the main text. \\ \hline
+
+  \texttt{/analysis/compare\_disorder.py} & \ref{section:rpi} & Measure quenched disorder for
   each trajectory in an ensemble of simulations, then plot distributions of quenched disorder.
@@
 
-  \texttt{/analysis/hbonds\_pairing.py} & \ref{M-section:rdouble} & Identify all hydrogen bonds
+  \texttt{/analysis/hbonds\_pairing.py} & \ref{section:rdouble} & Identify all hydrogen bonds
   then count the number of monomer pairs that share hydrogen bonds. \\ \hline
 
-  \texttt{/analysis/torsions.py} & \ref{M-section:slow_dynamics} & Calculate the autocorrelation
+  \texttt{/analysis/torsions.py} & \ref{section:slow_dynamics} & Calculate the autocorrelation
   function for a chosen dihedral. \\ \hline
@@
   gives a brief description of the purpose of each script.
-  }~\label{table:python_scripts}
+  }~\label{S-table:python_scripts_structure}
 
@@
 
-  \section{Attempted Self-assembly}\label{section:self_assembly}
+  \section{Attempted Self-assembly}\label{S-section:self_assembly}
 
   We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
-  generated using Packmol \cite{martinez_packmol:_2009} (Figure~\ref{fig:isotropic_box}).
+  generated using Packmol \cite{martinez_packmol:_2009} (Figure~\ref{S-fig:isotropic_box}).
   The input file given to Packmol is shown below.
@@
 
-  We use the nematic order parameter as defined in Section~\ref{method:nematic_order} to 
+  We use the nematic order parameter as defined in Section~\ref{S-method:nematic_order} to 
   observe any progress towards system ordering. In both cases, we see that the nematic
   order parameter stays close to zero for the duration of the simulation time, indicating
-  an isotropic arrangement of head groups (Figure~\ref{fig:nematic_isotropic}). The values
+  an isotropic arrangement of head groups (Figure~\ref{S-fig:nematic_isotropic}). The values
   are slightly negative since there are only 400 monomers. 
@@
   \includegraphics[width=\textwidth]{isotropic_box.png}
-  \caption{}\label{fig:isotropic_box}
+  \caption{}\label{S-fig:isotropic_box}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{nematic_isotropic.png}
-  \caption{}\label{fig:nematic_isotropic}
+  \caption{}\label{S-fig:nematic_isotropic}
   \end{subfigure}
@@
   parameter hovers close to zero for the duration of the simulation meaning the system
-  maintains its isotropic alignment.}\label{fig:self_assembly}
-  \end{figure}
-
-  \clearpage
-
-  \section{Monomer build procedure}\label{section:monomer_build_procedure}
-
-  Figure~\ref{fig:build_procedure} illustrates the procedure carried out by 
+  maintains its isotropic alignment.}\label{S-fig:self_assembly}
+  \end{figure}
+
+  \clearpage
+
+  \section{Monomer build procedure}\label{S-section:monomer_build_procedure}
+
+  Figure~\ref{S-fig:build_procedure} illustrates the procedure carried out by 
   \texttt{build.py} in order to build initial configurations.
@@
 		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
-		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{fig:build_procedure}
-  \end{figure}
-
-  \section{Number of monomers per column}\label{section:monomers_per_column}
+		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{S-fig:build_procedure}
+  \end{figure}
+
+  \section{Number of monomers per column}\label{S-section:monomers_per_column}
 
@@
   between stacked monomers persist throughout the entire correlation function (see
-  Figure~\ref{fig:correlation}). The correlation function of the system which we
+  Figure~\ref{S-fig:correlation}). The correlation function of the system which we
   built with 40 monomers per column is very similar to that created with 20 monomers
   per column (it continues to oscillate for its full length
-  (Figure~\ref{fig:tall_correlation_full})). If we continue adding monomers, the 
+  (Figure~\ref{S-fig:tall_correlation_full})). If we continue adding monomers, the 
   correlation function will eventually fully decay but it is not worth the 
@@
   \includegraphics[width=\textwidth]{z_correlation_overlay.png}
-  \caption{}\label{fig:z_correlation_overlay}
+  \caption{}\label{S-fig:z_correlation_overlay}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{tall_correlation_full.png}
-  \caption{}\label{fig:tall_correlation_full}
+  \caption{}\label{S-fig:tall_correlation_full}
   \end{subfigure}
@@
   system is ca. 17 nm tall so the full correlation function covers half this length
-  since periodicity forces the remaining length to be its mirror image.}\label{fig:correlation_functions}
+  since periodicity forces the remaining length to be its mirror image.}\label{S-fig:correlation_functions}
   \end{figure}
@@
 
-  \section{Initial Configuration Dependence}\label{section:initial_config_dependence}
+  \section{Initial Configuration Dependence}\label{S-section:initial_config_dependence}
 
@@
   groups are oriented in the parallel displaced and sandwiched configurations
-  (see Figure~\ref{fig:stacking}). Our model is most consistent with experiment
+  (see Figure~\ref{S-fig:stacking}). Our model is most consistent with experiment
   when built with 5 columns per pore, with monomers stacked 3.7 \AA~apart in 
@@
 
-  \subsection{Initial pore spacing}\label{section:initial_pore_spacing}
+  \subsection{Initial pore spacing}\label{S-section:initial_pore_spacing}
 
@@
   distance between the central axis of each pore with all others
-  (Figure~\ref{fig:p2p_diagram}). To reduce the number of variables, we held the
+  (Figure~\ref{S-fig:p2p_diagram}). To reduce the number of variables, we held the
   pore radius constant, at 5 \AA~and the distance between layers at 3.7 \AA~since
@@
 	columns are able to repel resulting in a large jump in pore spacing
-	(Figure~\ref{fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
+	(Figure~\ref{S-fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
 %		There is a large uncertainty in this value because the 1-4 pore spacing
-%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
+%		(Figure~\ref{S-fig:p2p_diagram}) deviates significantly from all other pore
 %		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
@@
 	repulsion of columns once the restraining potential is switched to 56 kJ
-	mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
+	mol$^{-1}$ nm$^{-2}$ (Figure~\ref{S-fig:p2p_41}). %After 400 ns, the
 %		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
 %		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
-%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
+%		(Figure~\ref{S-fig:p2p_diagram}) deviates significantly from all other pore
 %		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
@@
 	than the experimental value. This systems exhibits the smallest response to our 
- 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
+ 		equilibration procedure (Figure~\ref{S-fig:p2p_45}) and we chose to use this
         value for all our simulations in the main text.
@@
 	kJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
-	a linear trend (Figure~\ref{fig:p2p_50}).
+	a linear trend (Figure~\ref{S-fig:p2p_50}).
 %		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
@@
 	changes erratically until it begins to settle when the force constants are
-	below 3 kJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We recommend
+	below 3 kJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{S-fig:p2p_55}). We recommend
 	avoiding a system such as this where vacuum gaps between pore columns are
@@
 	\includegraphics[width=\textwidth]{p2p_diagram.png}
-	\caption{}~\label{fig:p2p_diagram}
+	\caption{}~\label{S-fig:p2p_diagram}
 %		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
@@
 		\vspace{-1.25em}
-		\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
+		\caption{39 \AA~initial pore spacing}~\label{S-fig:p2p_39}
 	\end{subfigure}
@@
 		\vspace{-1.25em}
-		\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
+		\caption{41 \AA~initial pore spacing}~\label{S-fig:p2p_41}
 	\end{subfigure}
@@
 		\vspace{-1.25em}
-		\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
+		\caption{45 \AA~initial pore spacing}~\label{S-fig:p2p_45}
 	\end{subfigure}
@@
 		\vspace{-1.25em}
-		\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
+		\caption{50 \AA~initial pore spacing}~\label{S-fig:p2p_50}
 	\end{subfigure}
@@
 		\vspace{-1.25em}
-		\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
+		\caption{55 \AA~initial pore spacing}~\label{S-fig:p2p_55}
 	\end{subfigure}
@@
 	when force constants are reduced below 3 kJ mol$^{-1}$ nm$^{-2}$. } 
-	\label{fig:p2p}
-  \end{figure}
-
-  \subsection{Initial pore radius}\label{section:initial_pore_radius}
+	\label{S-fig:p2p}
+  \end{figure}
+
+  \subsection{Initial pore radius}\label{S-section:initial_pore_radius}
 
   We tested 3 different pore radii, defined as shown in
-  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
+  Figure~\ref{S-fig:pore_radius_illustration}. For each system, we held the initial
   pore spacing constant at 45 \AA~and the initial stacking distance between monomers
   constant at 3.7 \AA. Equilibrated values of pore radii are presented in
-  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
+  Table~\ref{S-table:radii}. The pore radius in each simulation frame is calculated
   as the average distance of all carbonyl carbons (see
-  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
+  Figure~\ref{S-fig:pore_radius_illustration}) from their associated pore center.
   We generated statistics for the pore radii reported from the time series
   representing the average pore radius at each frame. We detected equilibration
-  as described in Section~\ref{M-method:equil_time} of the main text. We 
+  as described in Section~\ref{method:equil_time} of the main text. We 
   calculated the average and standard deviation of pore radii using only data 
@@
   full dry equilibration procedure, we see a combination of cylindrical and
-  slit-like pores (Figure~\ref{fig:slits}). Measuring the pore radius of this
+  slit-like pores (Figure~\ref{S-fig:slits}). Measuring the pore radius of this
   system does not have a concrete meaning since slits do not have a single
-  radius, but its calculated value is still reported in Table ~\ref{table:radii}. We
+  radius, but its calculated value is still reported in Table ~\ref{S-table:radii}. We
   are wary of such a non-symmetric structure and choose not to use a pore radius
@@
   \begin{tabular}{cc}
-  \toprule
+  \hline
   Initial Pore Radius & Equilibrated Pore Radius \\
-  \midrule
+  \hline
   2.5 \AA & $4.0 \pm 0.1$ \AA \\
@@
   8 \AA   & $6.9 \pm 0.1$ \AA \\
-  \bottomrule
+  \hline
   \end{tabular}
@@
 	  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
-	  the pore radius is too large, slit pores may form.}~\label{table:radii}
+	  the pore radius is too large, slit pores may form.}~\label{S-table:radii}
   \end{table}
@@
   R, based on the distance of the carbonyl carbon from the pore's
-  central axis.}~\label{fig:pore_radius_illustration}
+  central axis.}~\label{S-fig:pore_radius_illustration}
   \end{minipage}\qquad
@@
   here, sodium ions are colored blue, carbon atoms in the aromatic ring of the head 
-  group are colored orange and all else is colored cyan.}~\label{fig:slits}
+  group are colored orange and all else is colored cyan.}~\label{S-fig:slits}
   \end{minipage}
@@
 
-  \subsection{Initial stacking distance between monomers}\label{section:initial_dbwl}
+  \subsection{Initial stacking distance between monomers}\label{S-section:initial_dbwl}
 
@@
 
-  Figure~\ref{fig:dbwl_10} shows the structure of an assembly built
+  Figure~\ref{S-fig:dbwl_10} shows the structure of an assembly built
   with an initial layer spacing of 10 \AA~immediately after the restrained
@@
                 is equilibrated using the dry equilibration procedure, large vacuum gaps
-	form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
+	form as the monomers attempt to fill space.}\label{S-fig:dbwl_10} 
   \end{figure}
@@
   to occur in nature: sandwiched, parallel displaced and T-shaped
-  (Figures~\ref{fig:sandwiched}--\ref{fig:tshaped})~\cite{sinnokrot_estimates_2002}.
+  (Figures~\ref{S-fig:sandwiched}--\ref{S-fig:tshaped})~\cite{sinnokrot_estimates_2002}.
   We ruled out the T-shaped configuration because its vertical stacking distance is
@@
                 \includegraphics[width=\textwidth]{sandwiched.png}
-                \caption{}\label{fig:sandwiched}
+                \caption{}\label{S-fig:sandwiched}
         \end{subfigure}
@@
                 \includegraphics[width=\textwidth]{PD.png}
-                \caption{}\label{fig:pd}
+                \caption{}\label{S-fig:pd}
         \end{subfigure}
@@
                 \includegraphics[width=\textwidth]{Tshaped.png}
-                \caption{}\label{fig:tshaped}
+                \caption{}\label{S-fig:tshaped}
         \end{subfigure}
@@
                 \includegraphics[width=\textwidth]{sandwichedlayers.png}
-                \caption{}\label{fig:sandwichedlayers}
+                \caption{}\label{S-fig:sandwichedlayers}
         \end{subfigure}
@@
                 \includegraphics[width=\textwidth]{offsetlayers.png}
-                \caption{}\label{fig:offsetlayers}
-        \end{subfigure}
-        \caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
-        3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart.
+                \caption{}\label{S-fig:offsetlayers}
+        \end{subfigure}
+        \caption{(a) Sandwiched benzene dimers stack 3.8 \AA~apart. (b) Parallel-Displaced benzene dimers stack
+        3.4 \AA~vertically and 1.6 \AA~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \AA~apart.
         (d) Monomers stacked in the sandwiched configuration (e) Monomers stacked in the parallel-displaced
-        configuration.}\label{fig:stacking}
-  \end{figure}
-
-  Based on evidence from Section~\ref{M-section:rpi} of the main text, we
+        configuration.}\label{S-fig:stacking}
+  \end{figure}
+
+  Based on evidence from Section~\ref{section:rpi} of the main text, we
   believe it is most likely that the head groups stack somewhere between
-  the sandwiched and parallel displaced modes which we studied (Figure~\ref{fig:between_pd}).
+  the sandwiched and parallel displaced modes which we studied (Figure~\ref{S-fig:between_pd}).
 
@@
   \includegraphics[width=\textwidth]{pd_36.eps}
-  \caption{}\label{fig:pd_36}
+  \caption{}\label{S-fig:pd_36}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{pd_lt36.eps}
-  \caption{}\label{fig:pd_lt36}
+  \caption{}\label{S-fig:pd_lt36}
   \end{subfigure}
@@
   and 36 $\degree$. When $\theta$=0$\degree$, the system architecture is the same
-  as a sandwiched configuration.}\label{fig:between_pd}
-  \end{figure}
-
-  \section{Equilibration Details}\label{section:equilibration}
+  as a sandwiched configuration.}\label{S-fig:between_pd}
+  \end{figure}
+
+  \section{Equilibration Details}\label{S-section:equilibration}
 
@@
 
-  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
+  \section{Calculation of pore-to-pore spacing statistics}\label{S-section:p2p_stats}
 
@@
   We are interested in 5 pore-to-pore distances which should all be
-  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
+  equal in a perfect hexagonal array (Figure~\ref{S-fig:p2p_diagram}). Only 4 of
   the 5 distances are independent. We can calculate a trajectory of spacing
@@
   box vectors, however this technique does not fully capture the uncertainty
-  in the individual pore-to-pore distances (Table~\ref{table:p2p}).
+  in the individual pore-to-pore distances (Table~\ref{S-table:p2p}).
 
@@
   \begin{tabular}{ccc}
-  \toprule
+  \hline
   System                         & Pore Spacing ($nm$) & Pore Spacing ($nm$)              \\
                                  & Pore centers        & $\frac{1}{2}(x\ box\ vector)$ ($nm$) \\ 
-  \midrule
+  \hline
   Sandwiched, Ordered            & 4.18 $\pm$ 0.13     & 4.16 $\pm$ 0.01                  \\
@@
   Parallel Displaced, Disordered & 4.03 $\pm$ 0.07     & 4.01 $\pm$ 0.01                  \\
-  \bottomrule
+  \hline
   \end{tabular}
@@
   Both methods agree within uncertainty, but measuring the distance between pore centers
-  does a better job of showing the spread of pore-to-pore distances.}~\label{table:p2p}
+  does a better job of showing the spread of pore-to-pore distances.}~\label{S-table:p2p}
   \end{table}
@@
   peaks (the first two pairs of reflections from origin located at $|\mathbf{q}| 
-  \approx 0.18~\AA^{-1}$ and $|\mathbf{q}| \approx 0.31~\AA^{-1}$) are not visible
+  \approx 0.18~$\AA$^{-1}$ and $|\mathbf{q}| \approx 0.31~$\AA$^{-1}$) are not visible
   in the 2D WAXS pattern. The edges of the d\textsubscript{200} reflection (the third
-  pair of reflections located at $|\mathbf{q}| \approx 0.36~\AA^{-1}$) are slightly
+  pair of reflections located at $|\mathbf{q}| \approx 0.36~$\AA$^{-1}$) are slightly
   visible in the 2D WAXS pattern, so we used them to approximate the experimental
-  intensity of R-pores.}\label{fig:2DSAXS}
+  intensity of R-pores.}\label{S-fig:2DSAXS}
   \end{figure}
@@
 
-  \section{Component radial density functions}\label{section:radial_density}
+  \section{Component radial density functions}\label{S-section:radial_density}
  %BJC: can probably delete this figure 
@@
         \caption{Parallel Displaced, Ordered Pore Basin}
-        \label{fig:offset_density}
+        \label{S-fig:offset_density}
   \end{subfigure}
@@
         \caption{Sandwiched, Ordered Pore Basin}
-        \label{fig:layered_density}
+        \label{S-fig:layered_density}
   \end{subfigure}
@@
         \caption{Parallel Displaced, Disordered Pore Basin}
-        \label{fig:disordered_offset_density}
+        \label{S-fig:disordered_offset_density}
   \end{subfigure}
@@
         \caption{Sandwiched, Disordered Pore Basin}
-        \label{fig:disorder_layered_density}
+        \label{S-fig:disorder_layered_density}
   \end{subfigure}
@@
 	  concentrations of ions and head groups near the pore center, implying a more
-	  uniform, disordered pore.}~\label{fig:densities}
+	  uniform, disordered pore.}~\label{S-fig:densities}
   \end{figure}
@@
   \caption{The groups used for radial distribution calculations. Red atoms are in the
-  tails group. Green atoms are in the head group region. The blue atom is sodium.}\label{fig:monomer_color_coded}
+  tails group. Green atoms are in the head group region. The blue atom is sodium.}\label{S-fig:monomer_color_coded}
   \end{minipage}\qquad
@@
 %  height of the membrane in the z-direction.
-  }~\label{fig:rdf_diagram}
+  }~\label{S-fig:rdf_diagram}
   \end{minipage}
@@
 
-  \section{Ionic Conductivity}\label{section:ionic_conductivity}
+  \section{Ionic Conductivity}\label{S-section:ionic_conductivity}
  %BJC: add plot of collective diffusion values 
@@
   the collective diffusion model\cite{liu_collective_2013}, for robustness
-  (Figure~\ref{fig:conductivity}). The collective diffusion model measures the
+  (Figure~\ref{S-fig:conductivity}). The collective diffusion model measures the
   movement of the collective variable, Q, which is defined as the amount of
@@
         can be used for its calculation. For that reason, we use only the Nernst-Einstein relationship in the main text.}
-        \label{fig:conductivity}
-  \end{figure}
-
-  \section{Cross-linking algorithm details}\label{section:xlink}
+        \label{S-fig:conductivity}
+  \end{figure}
+
+  \section{Cross-linking algorithm details}\label{S-section:xlink}
 
   Crosslinking of the the monomer Na-GA3C11 occurs via a UV initiated free
-  radical polymerization (FRP) (Figure~\ref{fig:xlink_mech}). Head-to-tail addition
+  radical polymerization (FRP) (Figure~\ref{S-fig:xlink_mech}). Head-to-tail addition
   takes place between terminal vinyl groups on each of the monomer tails. We
@@
 	  radicals react with the vinyl groups of other monomers in order to propagate
-	  crosslinking.}\label{fig:xlink_mech}
+	  crosslinking.}\label{S-fig:xlink_mech}
   \end{figure}
@@
   \clearpage
-  \section{The nematic order parameter}\label{method:nematic_order}
+  \section{The nematic order parameter}\label{S-method:nematic_order}
 
@@
   $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
-  the aromatic head groups ($\mathbf{v}$ in Figure~\ref{fig:director}).
+  the aromatic head groups ($\mathbf{v}$ in Figure~\ref{S-fig:director}).
 
@@
   \caption{We calculate the nematic order parameter by measuring the angle
-  between $\mathbf{v}$ and the $z$-axis.}~\label{fig:director}
+  between $\mathbf{v}$ and the $z$-axis.}~\label{S-fig:director}
   \end{figure}
@@
   The nematic order parameter is highest in sandwiched systems. 
-  Figure~\ref{fig:nematic_distribution} shows the distribution of angles between
+  Figure~\ref{S-fig:nematic_distribution} shows the distribution of angles between
   the nematic director and the vector perpendicular to the monomer head groups. 
@@
                 \includegraphics[width=\linewidth]{layered_nematic_order.png}
-                \caption{Sandwiched, Ordered}~\label{fig:sandwich_nematic}
+                \caption{Sandwiched, Ordered}~\label{S-fig:sandwich_nematic}
         \end{subfigure}%
@@
                 \includegraphics[width=\linewidth]{offset_nematic_order.png}
-                \caption{Parallel Displaced, Ordered}~\label{fig:offset_nematic}
+                \caption{Parallel Displaced, Ordered}~\label{S-fig:offset_nematic}
         \end{subfigure}
@@
                 \includegraphics[width=\linewidth]{disorder_sandwich_nematic_order.png}
-                \caption{Sandwiched, Disordered}~\label{fig:disorder_sandwich_nematic}
+                \caption{Sandwiched, Disordered}~\label{S-fig:disorder_sandwich_nematic}
         \end{subfigure}%
@@
                 \includegraphics[width=\linewidth]{disorder_offset_nematic_order.png}
-                \caption{Parallel Displaced, Disordered}~\label{fig:disorder_offset_nematic}
+                \caption{Parallel Displaced, Disordered}~\label{S-fig:disorder_offset_nematic}
         \end{subfigure}
@@
   \caption{The distribution of angles between nematic director vector (see
-	  Figure~\ref{fig:director}) and the $z$-axis averaged over the equilibrated portion
+	  Figure~\ref{S-fig:director}) and the $z$-axis averaged over the equilibrated portion
 	  of each trajectory. The ordered sandwiched configuration has a higher nematic order
@@
 	  sandwiched configuration has a higher nematic order parameter than the 
-	  disordered parallel displaced configuration.}~\label{fig:nematic_distribution}
+	  disordered parallel displaced configuration.}~\label{S-fig:nematic_distribution}
   \end{figure}
@@
 %BJC: now in main text
-%  \section{Measurement of intensities of experimental and simulated XRD patterns}\label{section:xrd_intensities}
+%  \section{Measurement of intensities of experimental and simulated XRD patterns}\label{S-section:xrd_intensities}
 %  
@@
 %  used to calculate the average intensity of R-alkanes is shown in 
-%  Figure~\ref{fig:ralkanes}. The top region is excluded because, in the simulated
+%  Figure~\ref{S-fig:ralkanes}. The top region is excluded because, in the simulated
 %  patterns, R-$\pi$ intersects with R-alkanes.
@@
 %  R-$\pi$ and R-double are reported as the maximum values of the peaks of the 
-%  $q_z$ cross-section of the experimental pattern at $q_r=0$ (Figure~\ref{fig:rpi_rdouble}).
+%  $q_z$ cross-section of the experimental pattern at $q_r=0$ (Figure~\ref{S-fig:rpi_rdouble}).
 %  In the case of the experimental pattern, the peak heights are not symmetrical,
@@
 %  selected by visual inspection. We report the average intensity within the regions 
-%  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernible
+%  highlighted in red in Figure~\ref{S-fig:rspots}. If there are no easily discernible
 %  spots, we report the average intensity at the intersection of R-alkanes with
@@
 
-  \section{Pore radius as a function of monomers per column}\label{section:pore_radius}
+  \section{Pore radius as a function of monomers per column}\label{S-section:pore_radius}
 
@@
   \end{subfigure}
-  \caption{The pore radius increases as we increase the number of columns per pore.}\label{fig:pore_radius}
-  \end{figure}
-
-  \section{Noise in simulated diffraction patterns}\label{section:xrd_noise}
+  \caption{The pore radius increases as we increase the number of columns per pore.}\label{S-fig:pore_radius}
+  \end{figure}
+
+  \clearpage
+  \section{Noise in simulated diffraction patterns}\label{S-section:xrd_noise}
 
   The magnitude of noise in the simulated diffraction patterns decreases as 
-  the number of independent configurations increases (Figure~\ref{fig:xrd_noise}).
+  the number of independent configurations increases (Figure~\ref{S-fig:xrd_noise}).
   We simulated the structure factor of 100 randomly placed particles and varied 
@@
   \caption{The magnitude of noise, especially along $q_r$=0, decreases
-  as the number of independent configurations (N) increases.}\label{fig:xrd_noise}
-  \end{figure}
-
-  \clearpage
-%  \section{Experimental correlation length of R-$\pi$}\label{section:correlation_length}
+  as the number of independent configurations (N) increases.}\label{S-fig:xrd_noise}
+  \end{figure}
+
+  \clearpage
+%  \section{Experimental correlation length of R-$\pi$}\label{S-section:correlation_length}
 % 
@@
 %  from the raw 2D WAXS data. We took a slice of the 2D WAXS data along the dashed line in
-%  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
+%  Figure ~\ref{S-fig:waxs_dashed}. We removed background noise by subtracting the
 %  intensity far from the pattern (high $q$) uniformly. We used a least squares
@@
 %  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
-%  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
+%  R-alkanes (Figure~\ref{S-fig:correlation_length_exp}). The full width at half
 %  maximum (FWHM) is related to the correlation length, L, by the relationship: $
@@
 
-  \section{The effect of imposed tail tilt}\label{section:tail_tilt}
+  \section{The effect of imposed tail tilt}\label{S-section:tail_tilt}
 
@@
   the tails begin to tend towards a negligible tilt angle
-  (Figure~\ref{fig:tail_tilt}).
+  (Figure~\ref{S-fig:tail_tilt}).
 
@@
   angle with respect to the membrane plane decreases until it is nearly
-  negligible.}\label{fig:tail_tilt}
-  \end{figure}
-
-  \section{Tail organization}\label{section:tail_packing}
+  negligible.}\label{S-fig:tail_tilt}
+  \end{figure}
+
+  \section{Tail organization}\label{S-section:tail_packing}
 
@@
   the tails. We divided the tail into three sections: tail-fronts, tail-middles
-  and tail-ends. The sections are illustrated in Figure~\ref{fig:tail_sections}.
+  and tail-ends. The sections are illustrated in Figure~\ref{S-fig:tail_sections}.
 
@@
   \caption{We divided the tail into three regions: tail-fronts (blue), 
-  tail-middles (green) and tail-ends (red).}\label{fig:tail_sections}
+  tail-middles (green) and tail-ends (red).}\label{S-fig:tail_sections}
   \end{figure}
@@
   between each center of mass and its nearest neighbor center of masses of the
-  same tail section. For example, Figure~\ref{fig:centroids} shows a 3D plot of
+  same tail section. For example, Figure~\ref{S-fig:centroids} shows a 3D plot of
   the center of masses of each tail front. We wanted to know the average location
   of nearest neighbors to each center of mass. The red bead in 
-  Figure~\ref{fig:centroids} is a randomly selected center of mass. The
+  Figure~\ref{S-fig:centroids} is a randomly selected center of mass. The
   green beads are the nearest neighbor center of masses to the red bead. We
@@
   each simulation frame and were able to plot the average distribution shown
-  in Figure~\ref{fig:tail_fronts}. We repeated the calculation for the tail
-  middles (Figure~\ref{fig:tail_middles}) and the tail ends 
-  (Figure~\ref{fig:tail_ends}). The amount of order decreases as we explore
+  in Figure~\ref{S-fig:tail_fronts}. We repeated the calculation for the tail
+  middles (Figure~\ref{S-fig:tail_middles}) and the tail ends 
+  (Figure~\ref{S-fig:tail_ends}). The amount of order decreases as we explore
   packing of tails farther from the head group.
@@
         \includegraphics[width=\textwidth]{centroids.png}
-		\caption{}\label{fig:centroids}
+		\caption{}\label{S-fig:centroids}
         \end{subfigure}
@@
         \includegraphics[width=\textwidth]{hexagonal_tail_packing.png}
-        \caption{}\label{fig:tail_fronts}
+        \caption{}\label{S-fig:tail_fronts}
         \end{subfigure}
@@
         \includegraphics[width=\textwidth]{hexagonal_tail_packing_middles.png}
-        \caption{}\label{fig:tail_middles}
+        \caption{}\label{S-fig:tail_middles}
         \end{subfigure}
@@
         \includegraphics[width=\textwidth]{hexagonal_tail_packing_ends.png}
-        \caption{}\label{fig:tail_ends}
+        \caption{}\label{S-fig:tail_ends}
         \end{subfigure}
         \caption{Monomer tails pack together hexagonally. (a) The center of mass
-        of each tail-front (See Figure~\ref{fig:tail_sections}) is visualized as
+        of each tail-front (See Figure~\ref{S-fig:tail_sections}) is visualized as
         a blue sphere. The red sphere highlights an example of a tail-front 
@@
         There is far less order at the ends of the tails where there is more
-        space to fill.}\label{fig:tail_packing}
-  \end{figure}
-
-  \clearpage
-
-  \section{Correlation Functions}\label{section:correlation_functions}
+        space to fill.}\label{S-fig:tail_packing}
+  \end{figure}
+
+  \clearpage
+
+  \section{Correlation Functions}\label{S-section:correlation_functions}
 
@@
   \includegraphics[width=\textwidth]{z_correlation_sandwich.pdf}
-  \caption{Sandwiched, Ordered Basin}\label{fig:z_correlation_sandwich}
+  \caption{Sandwiched, Ordered Basin}\label{S-fig:z_correlation_sandwich}
   \end{subfigure}  
@@
   \includegraphics[width=\textwidth]{z_correlation_offset.pdf}
-  \caption{Parallel Displaced, Ordered Basin}\label{fig:z_correlation_offset}
+  \caption{Parallel Displaced, Ordered Basin}\label{S-fig:z_correlation_offset}
   \end{subfigure}  
@@
   \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.pdf}
-  \caption{Sandwiched, Disordered Basin}\label{fig:z_correlation_sandwich_disordered}
+  \caption{Sandwiched, Disordered Basin}\label{S-fig:z_correlation_sandwich_disordered}
   \end{subfigure}  
@@
   \includegraphics[width=\textwidth]{z_correlation_offset_disordered.pdf}
-  \caption{Parallel Displaced, Disordered Basin}\label{fig:z_correlation_offset_disordered}
+  \caption{Parallel Displaced, Disordered Basin}\label{S-fig:z_correlation_offset_disordered}
   \end{subfigure}  
@@
 	  fitting a decaying exponential function
-	  (Equation~\ref{M-eqn:decaying_exponential} of the main text) to the peaks of $g(z)$. The
+	  (Equation~\ref{eqn:decaying_exponential} of the main text) to the peaks of $g(z)$. The
 	  correlation length is longer for ordered basin systems
-	  (Table~\ref{M-table:correlation_length} of the main text). We did not attempt to calculate the
+	  (Table~\ref{table:correlation_length} of the main text). We did not attempt to calculate the
 	  correlation length for (d) because there are no clear peaks. We assume that
 	  this correlation length is less than the vertical distance between
-	  monomers.}\label{fig:correlation}
+	  monomers.}\label{S-fig:correlation}
   \end{figure}
@@
   $z$-slices within 2.1~\AA~of the center of the correlation function 
-  (see Section~\ref{M-section:correlation_length}), $g(z)$ shows oscillatory 
+  (see Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
   behavior and its correlation length nearly triples to 12.4 $\pm$ 0.7 \AA.
-  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
+  (Figure~\ref{S-fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
   reinforced by head groups in neighboring columns which is not expected
@@
   correlation length of the ordered sandwich configuration nearly triples compared 
-  to that shown in Figure~\ref{fig:z_correlation_sandwich}.}\label{fig:z_correlation_fullbox}
-  \end{figure}
-
-  \section{Structure factors of simplified systems}\label{section:simplified_sf}
-
-  In the Section~\ref{M-section:rpi} of the main text, we used simplified systems
+  to that shown in Figure~\ref{S-fig:z_correlation_sandwich}.}\label{S-fig:z_correlation_fullbox}
+  \end{figure}
+
+  \section{Structure factors of simplified systems}\label{S-section:simplified_sf}
+
+  In the Section~\ref{section:rpi} of the main text, we used simplified systems
   made up of point scatterers in order to understand the main factors that influence
@@
   columns in the $z$-direction by 12\% and 27\%, we saw a 3 and 15-fold decrease in
-  the maximum intensity of R-$\pi$ respectively (Figure~\ref{fig:intensity_vs_zsigma}).
+  the maximum intensity of R-$\pi$ respectively (Figure~\ref{S-fig:intensity_vs_zsigma}).
   Despite the decrease in intensity, the 3 cross-sections have the same shape 
-  (Figure~\ref{fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
+  (Figure~\ref{S-fig:rpi_xsection_vs_zsigma}), whose sharp Bragg-like peaks are
   not consistent with experiment.
@@
   \includegraphics[width=\textwidth]{intensity_vs_zsigma.pdf}
-  \caption{}\label{fig:intensity_vs_zsigma}
+  \caption{}\label{S-fig:intensity_vs_zsigma}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.pdf}
-  \caption{}\label{fig:rpi_xsection_vs_zsigma}
+  \caption{}\label{S-fig:rpi_xsection_vs_zsigma}
   \end{subfigure}
@@
   of 15 when we increase $\sigma_z$ by 27\% (red). (b) Although the maximum intensity of R-$\pi$
-  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{fig:znoise}
+  decreases with increasing $\sigma_z$, the peak shape remains the same.}\label{S-fig:znoise}
   \end{figure}
@@
   $\theta$ directions by multiplying their values by a factor of 0.5 and 2
-  (Figure~\ref{fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
+  (Figure~\ref{S-fig:qy_fwhm}). When we cut the noise in half, the FWHM increases
   by 88\%. When we double the noise, the FWHM decreases by 51\%. As we have fit
@@
 	  we double the disorder (Noise factor = 2), the FWHM decreases by
-	  51\%.}\label{fig:qy_fwhm}
-  \end{figure}
-
-  \section{Ensemble of ordered sandwiched configurations}\label{section:sandwiched_ensemble}
-
-  Here we show the results of the same analysis shown in Figures~\ref{M-fig:ensemble_XRD} 
-  and~\ref{M-fig:full_ensemble_distributions} of the main text for the 
+	  51\%.}\label{S-fig:qy_fwhm}
+  \end{figure}
+
+  \clearpage
+  \section{Ensemble of ordered sandwiched configurations}\label{S-section:sandwiched_ensemble}
+
+  Here we show the results of the same analysis shown in Figures~\ref{fig:ensemble_XRD} 
+  and~\ref{fig:full_ensemble_distributions} of the main text for the 
   ordered sandwiched ensemble of configurations.
@@
   \caption{Distributions of deviations from ideal positions generated with data
-  from all independent simulations}\label{fig:offset_ensemble_pooled}
+  from all independent simulations}\label{S-fig:offset_ensemble_pooled}
   \end{subfigure}
@@
   \caption{Empirical cumulative distribution functions generated from (a) and
-  from simulation ensembles.}\label{fig:offset_ecdfs}
+  from simulation ensembles.}\label{S-fig:offset_ecdfs}
   \end{subfigure}
@@
   deviations than the mean deviations of distributions sampled from the full
-  distribution.}\label{fig:full_ensemble_distributions}
+  distribution.}\label{S-fig:full_ensemble_distributions}
   \end{figure}
@@
   \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.pdf}
-  \caption{}\label{fig:offset_ensemble_stds}
+  \caption{}\label{S-fig:offset_ensemble_stds}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{sandwiched_ensemble_means.pdf}
-  \caption{}\label{fig:offset_ensemble_means}
+  \caption{}\label{S-fig:offset_ensemble_means}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{sandwiched_ensemble_regional_density.pdf}
-  \caption{}\label{fig:offset_ensemble_regional_density}
+  \caption{}\label{S-fig:offset_ensemble_regional_density}
   \end{subfigure}
@@
   main system simulation trajectory (black lines) and from the ensemble of 
-  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
+  trajectories (all other lines) look qualitatively similar.}\label{S-fig:ensemble_stds}
   \end{figure}
@@
   head groups to stay coplanar with the phenyl group to which it is attached
-  (Figure~\ref{fig:carboxylate_dihedral_rb}). Although GAFF may over-predict the penalty
+  (Figure~\ref{S-fig:carboxylate_dihedral_rb}). Although GAFF may over-predict the penalty
   for deviating from its minimum energy configuration relative to those calculated 
@@
   penalty as the dihedral becomes antiparallel to the plane of the aromatic 
-  ring.}\label{fig:carboxylate_dihedral_rb}
+  ring.}\label{S-fig:carboxylate_dihedral_rb}
   \end{figure}
@@
 %                \includegraphics[width=\textwidth]{water_filled_pore.png}
-%                \caption{}\label{fig:water_filled_pores}
+%                \caption{}\label{S-fig:water_filled_pores}
 %        \end{subfigure}
@@
 %                \includegraphics[width=\textwidth]{water_removed.png}
-%                \caption{}\label{fig:water_removed}
+%                \caption{}\label{S-fig:water_removed}
 %        \end{subfigure}
@@
 %	  visualized with water molecules and sodium ions removed. Head groups vacate the
-%	  pore region leaving an aqueous solution of water and sodium ions.}\label{fig:water_pores}
+%	  pore region leaving an aqueous solution of water and sodium ions.}\label{S-fig:water_pores}
 %  \end{figure}
@@
 % BJC: a lot of this is in the main text, but there is some other potentially usefull stuff in here
-%  \section{Demonstrative Fourier transforms}\label{section:fourier}
+%  \section{Demonstrative Fourier transforms}\label{S-section:fourier}
 %  
@@
 %
-%  \subsection{Magnitude of R-$\pi$}\label{section:rpi_ft}
+%  \subsection{Magnitude of R-$\pi$}\label{S-section:rpi_ft}
 %  
@@
 %  Persistent oscillations in the z-correlation function, $g(z)$, increase the intensity of R-$\pi$. 
-%  In Figure~\ref{fig:z_correlation}, we fit a decaying sinusoidal function 
-%  (equation~\ref{M-eqn:decaying_sinusoid} of the main text) to $g(z)$ calculated from the
+%  In Figure~\ref{S-fig:z_correlation}, we fit a decaying sinusoidal function 
+%  (equation~\ref{eqn:decaying_sinusoid} of the main text) to $g(z)$ calculated from the
 %  sandwiched configuration in the ordered basin. While the sinusoidal decay fit decays to one
 %  rather quickly, $g(z)$ continues to oscillate with nearly the same amplitude as its third peak. 
-%  In Figure~\ref{fig:theoretical_correlation_functions}, we overlay the same decaying sinusoidal
+%  In Figure~\ref{S-fig:theoretical_correlation_functions}, we overlay the same decaying sinusoidal
 %  fit with a function that continues to oscillate with the same amplitude as the third peak of
-%  the fit to $g(z)$. In Figure~\ref{fig:power_spectrum_comparison}, we plot the power spectrum
-%  generated from the discrete Fourier transform of the plots in Figure~\ref{fig:theoretical_correlation_functions}. 
+%  the fit to $g(z)$. In Figure~\ref{S-fig:power_spectrum_comparison}, we plot the power spectrum
+%  generated from the discrete Fourier transform of the plots in Figure~\ref{S-fig:theoretical_correlation_functions}. 
 %  The maximum intensity of the power spectrum increases by nearly 60\% when the correlation 
@@
 %  \includegraphics[width=\textwidth]{z_correlation_layered_sinefit.png}
-%  \caption{}\label{fig:z_correlation}
+%  \caption{}\label{S-fig:z_correlation}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{theoretical_correlation_functions.png}
-%  \caption{}\label{fig:theoretical_correlation_functions}
+%  \caption{}\label{S-fig:theoretical_correlation_functions}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{power_spectrum_comparison.png}
-%  \caption{}\label{fig:power_spectrum_comparison}
+%  \caption{}\label{S-fig:power_spectrum_comparison}
 %  \end{subfigure}
@@
 %  as its third peak. (c) The power spectrum of each plot in (b) exhibits a 60\% increase in
-%  intensity of the peaks when the function does not decay to 1.}\label{fig:rpi_ft}
+%  intensity of the peaks when the function does not decay to 1.}\label{S-fig:rpi_ft}
 %  \end{figure}
 %  
-%  \subsection{Simplified assemblies}\label{section:simplified_assemblies}
+%  \subsection{Simplified assemblies}\label{S-section:simplified_assemblies}
 %  
@@
 %  every 7.4 $\AA$. This line of thought gave rise to the systems studied in 
-%  section~\ref{M-section:rdouble} of the main text.
+%  section~\ref{section:rdouble} of the main text.
 %  
@@
 %  \includegraphics[width=\textwidth]{simple_sandwich_realspace.png}
-%  \caption{}\label{fig:simple_sandwich_realspace}
+%  \caption{}\label{S-fig:simple_sandwich_realspace}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{simple_sandwich_rzplot.png}
-%  \caption{}\label{fig:simple_sandwich_rzplot}
+%  \caption{}\label{S-fig:simple_sandwich_rzplot}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{simple_offset_realspace.png}
-%  \caption{}\label{fig:simple_offset_realspace}
+%  \caption{}\label{S-fig:simple_offset_realspace}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{simple_offset_rzplot.png}
-%  \caption{}\label{fig:simple_offset_rzplot}
-%  \end{subfigure}
-%  \caption{}\label{fig:simple_FTs}
+%  \caption{}\label{S-fig:simple_offset_rzplot}
+%  \end{subfigure}
+%  \caption{}\label{S-fig:simple_FTs}
 %  \end{figure}
 
-  \section{All solvated systems}\label{section:solvation}
+  \section{All solvated systems}\label{S-section:solvation}
 
@@
 	of water increase discrepancies with experiment} %MRS7:by increasing disorder?
-  \label{fig:solvation}
-
-  \end{figure}
-
-  \clearpage
-  \section{The role of water in the appearance of R-double}\label{section:rdouble}
+  \label{S-fig:solvation}
+
+  \end{figure}
+
+  \clearpage
+  \section{The role of water in the appearance of R-double}\label{S-section:rdouble}
 
@@
   vertically stacked monomer pairs share hydrogen bonds with a common water molecule (See
-  Section~\ref{M-section:rdouble} of the main text). It is not a consequence of the 
+  Section~\ref{section:rdouble} of the main text). It is not a consequence of the 
   structure of water itself because R-double still persists if we removed water from 
-  the trajectory which gives rise to the feature (Figure~\ref{fig:rdouble_water_removed}). 
+  the trajectory which gives rise to the feature (Figure~\ref{S-fig:rdouble_water_removed}). 
   We quantified the occurence of pairing interactions by binning the $z$-positions of the center of mass of 
@@
   columns in our system. Peaks in the distributions represent the scenario where a monomer head group
-  shares a water molecule with a head group vertically above it (See Figure~\ref{fig:pore_hbonds}).
-  We calculated the discrete Fourier transform of the distributions in Figure~\ref{fig:pore_hbonds}
+  shares a water molecule with a head group vertically above it (See Figure~\ref{S-fig:pore_hbonds}).
+  We calculated the discrete Fourier transform of the distributions in Figure~\ref{S-fig:pore_hbonds}
   which we used as a rough indicator of whether the head group arrangement will lead to R-double
-  (Figure~\ref{fig:pore_hbonds_ft}). We see the strongest indicator of asymmetric monomer
-  stacking in Pore 1 where the peaks at 0.76 $\AA^{-1}$ are clearly distinguishable, meaning
+  (Figure~\ref{S-fig:pore_hbonds_ft}). We see the strongest indicator of asymmetric monomer
+  stacking in Pore 1 where the peaks at 0.76 \AA$^{-1}$ are clearly distinguishable, meaning
   there is periodicity at twice the $\pi$-stacking distance.
@@
   R-double is still present since it is the result of uneven spacing between 
-  head groups.}\label{fig:rdouble_water_removed}
+  head groups.}\label{S-fig:rdouble_water_removed}
   \end{figure}
@@
   \includegraphics[width=\textwidth]{pore_hbonds.png}
-  \caption{}\label{fig:pore_hbonds}
+  \caption{}\label{S-fig:pore_hbonds}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
-  \caption{}\label{fig:pore_hbonds_ft}
+  \caption{}\label{S-fig:pore_hbonds_ft}
   \end{subfigure}
@@
   performed discrete Fourier transforms on each distribution in (a) In Pore 1, there 
-  is periodicity every 8.3 $\AA$, twice the $\pi$-stacking distance, as indicated by the
-  intensity at 0.76 $\AA^{-1}$. In this case, the center of mass of two adjacent pairs 
+  is periodicity every 8.3 \AA, twice the $\pi$-stacking distance, as indicated by the
+  intensity at 0.76 \AA$^{-1}$. In this case, the center of mass of two adjacent pairs 
   is separated by twice the average monomer stacking distance, while the four monomers 
   involved are unequally spaced. These conditions seem likely to give rise to R-double.
-  }\label{fig:hbonds}
+  }\label{S-fig:hbonds}
   \end{figure}
@@
   the slope of the linear region of their mean squared displacement curves accumulated
-  over the length of the equilibration simulations (Table~\ref{table:msd}).
+  over the length of the equilibration simulations (Table~\ref{S-table:msd}).
 
@@
   \begin{tabular}{cc}
-  \toprule
+  \hline
   System & Diffusion Constant ($m^2/s$) \\ 
-  \midrule
+  \hline
   Sandwiched, Ordered & $1.4 \times 10^{-14}$ \\
@@
   Parallel Displaced, 1 wt \% water & $7.1 \times 10^{-14}$ \\
-  \bottomrule
+  \hline
   \end{tabular}
   \caption{The diffusion constants for all systems are on the order of $10^{-14} m^2/s$ 
-  .}~\label{table:msd}
+  .}~\label{S-table:msd}
   \end{table}
@@
 
-  In Section~\ref{M-section:slow_dynamics} of the main text, we calculated the
+  In Section~\ref{section:slow_dynamics} of the main text, we calculated the
   autocorrelation function of the outer tail either dihedrals pictured
-  in Figure~\ref{fig:dihedral_illustration}. The plots of the autocorrelation
-  functions versus time lag are shown in Figure~\ref{fig:dihedral}.
+  in Figure~\ref{S-fig:dihedral_illustration}. The plots of the autocorrelation
+  functions versus time lag are shown in Figure~\ref{S-fig:dihedral}.
 
@@
   since the position of the center tail leads to fundamentally different interactions and
-  dynamics.}\label{fig:dihedral_illustration}
+  dynamics.}\label{S-fig:dihedral_illustration}
   \end{figure}
@@
   	\includegraphics[width=\textwidth]{dihedral_autocorrelation_300K.pdf}
-  	\caption{300K}\label{fig:dihedrals_300K}
+  	\caption{300K}\label{S-fig:dihedrals_300K}
   \end{subfigure}
@@
   	\includegraphics[width=\textwidth]{dihedral_autocorrelation_500K.pdf} % Run : torsions.py -t tethered_columns.xtc -g tethered_columns.gro (the appropriate dihedral is the default)
-  	\caption{500K}\label{fig:dihedrals_500K}
+  	\caption{500K}\label{S-fig:dihedrals_500K}
   \end{subfigure}
@@
   (b) The ether dihedrals become decorrelated after 11 ns when the temperature
-  of the system is increased to 500 K.}\label{fig:dihedral}
+  of the system is increased to 500 K.}\label{S-fig:dihedral}
   \end{figure}
@@
 %  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
-%  \caption{}\label{fig:rdouble_offset_solvated_rzplot}
+%  \caption{}\label{S-fig:rdouble_offset_solvated_rzplot}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{rzplot_pore1_removed.png}
-%  \caption{}\label{fig:rzplot_pore1_removed}
+%  \caption{}\label{S-fig:rzplot_pore1_removed}
 %  \end{subfigure}
@@
 %  parallel displaced configuration with 1 wt\% water shows R-double at $mathbf{q}=(0, 0.7) \AA^{-1}$.
-%  (b) When we remove }\label{fig:pore1_removed}
+%  (b) When we remove }\label{S-fig:pore1_removed}
 %  \end{figure}
@@
 
-  \section{Influence of Cross-linking on physical properties}\label{section:xlink_physical}
+  \section{Influence of Cross-linking on physical properties}\label{S-section:xlink_physical}
 
@@
   and decreases in the parallel displaced configuration. The correlation length decreases
-  in both configurations.}\label{fig:xlink}
-  \end{figure}
-
-\clearpage
-\bibliography{llc}
-\end{document}
-
-% LocalWords:  Na GA Packmol pdb filetype MarvinSketch noauthor nodate GROMACS
-% LocalWords:  atomtypes antechamber inpcrd prmtop acpype py silva gro gmx NVT
-% LocalWords:  editconf molcharge bccsym cyan png dihedrals pore's ca pt xy kJ
-% LocalWords:  kinetically metastable outlier BJC Berendsen barostat Parrinello
-% LocalWords:  Rahman solvated solvate Eq XRD alkanes WAXS exp FWHM mon alkane
-% LocalWords:  transitioning topview rzplot traj binned wt LLC Subharmonics UV
-% LocalWords:  realspace Crosslinking polymerization FRP crosslinking FRPs rb
-% LocalWords:  racemic Nernst carboxylate antiparallel llc
+  in both configurations.}\label{S-fig:xlink}
+  \end{figure}

### 2020-02-12 Ben_Manuscripts/thesis/thesis.tex
starting dissertation

\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
%\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{textcomp} % gets rid of \perthousand and \micro warnings that come from gensymb
\usepackage{gensymb}
\usepackage{subcaption}
\usepackage{tcolorbox}
\usepackage[export]{adjustbox}
\usepackage{listings}

\DeclareUnicodeCharacter{03C9}{$\omega$}
\DeclareUnicodeCharacter{03C0}{$\pi$}

\definecolor{amber}{rgb}{0.99, 0.76, 0.0} % golden poppy

\title{Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations}

\author{Benjamin Joseph}{Coscia}

\otherdegrees{B.A., University of Connecticut, 2014 \\
	          M.S., University of Colorado Boulder, 2017}

\Degree{Doctor of Philosophy}		                %  #1 {long descr.}
	   {Ph.D., Chemical Engineering}		%  #2 {short descr.}

\dept{Department of}			                %  #1 {designation}
	 {Chemical and Biological Engineering}		%  #2 {name}

\advisor{Prof.}				        %  #1 {title}
	    {Michael Shirts}			%  #2 {name}

\reader{Prof. Richard Noble}		%  2nd person to sign thesis
\readerThree{Prof. Douglas Gin}		%  3rd person to sign thesis
\readerFour{Prof. Matthew Glaser}
\readerFive{Prof. Robert Davis}

\abstract{

  % \OnePageChapter	% use if abstract is less than one page

  % BJC: spliced together abstracts from papers with some additions

  The ability to perform highly selective aqueous separations at low cost
  is beneficial to a variety of chemical industries

  Periodic, nanostructured porous polymer membranes made from the cross-linked
  inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
  a promising class of materials for selective separations.

  The uniform size and complex chemical topology of the pores formed by
  self-assembled amphiphilic molecules such as liquid crystals make them
  promising candidates for selective separations.

  In this work, we investigate an experimentally characterized LLC polymer 
  membrane using atomistic molecular modeling. We

  First, we gained a deep understanding of nanoscopic pore structure in order 
  to make sure we got the chemical environment in the pores correct.

  In particular, we compare simulated X-ray
  diffraction (XRD) patterns with experimental XRD data to quantify and
  understand the differences between simulation and experiment.

%  We find that the
%  nanopores are likely composed of 5 columns of stacked LLC monomers which
%  surround each hydrophilic core. Evidence suggests that these columns likely
%  move independently of each other over longer time scales than accessible via
%  atomistic simulation. We also find that WAXS structural features previously
%  attributed to monomer tail tilt is likely instead due to ordered tail packing.
%  Although this system has been reported as dry, we show that small amounts of
%  water are necessary to reproduce all features from the experimental XRD pattern
%  due to asymmetries introduced by hydrogen bonds between the monomer head groups
%  and water molecules.

  Finally, we explore the composition and structure of the
  nanopores and reveal that there exists a composition gradient rather than an
  abrupt partition between the hydrophilic and hydrophobic regions. A caveat is
  that the time scales of the dynamics are extremely long for this system,
  resulting in simulated structures that appear too ordered, thus requiring
  careful examination of the metastable states observed in order to draw any
  conclusions.

  %The clearer picture of the nanoscopic structure of these membranes
  %provided in this study will enable a better understanding of the mechanisms of
  %small molecule transport within these nanopores.

  We observe transport of water, sodium ions and 20 small polar
  solutes within the pores of a lyotropic liquid crystal (LLC) membrane using
  atomistic molecular simulations. We find that the transport of a species is
  dependent not only on molecular size, but on chemical functionality as well.
%  The membrane's inhomogeneous composition gives rise to radially dependent
%  transport mechanisms with respect to the pore centers. 
  We observe that all
  solutes perform intermittent hops between lengthy periods of entrapment. Three
  different trapping mechanisms are responsible for this behavior. First, solutes
  that drift out of the pore can become entangled among the dense monomer tails.
  Second, solutes can donate hydrogen bonds to the monomer head groups. Third,
  solutes can coordinate with sodium counter ions. The degree to which a solute
  is affected by each mechanism is dependent on the chemical functionality of the
  solute.

  %Using the insights developed in this study, we can begin to think about
  %how to redesign existing LLC membranes in order to perform solute-specific
  %separations.

  Mathematically modeling complex transport phenomena at the molecular level
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC)
  membrane, in order to predict solute mean squared displacements (MSDs)
  and solute flux, and thus solute selectivity, in macroscopic length pores.

  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time
  random walk. From the MD simulations, we parameterize the distribution of
  dwell times, hop lengths between dwells and correlation between hops. We
  explore two variations of the anomalous diffusion modeling approach. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies two sets of parameters based on the solute's radial distance from the
  closest pore center.

  Next, we generalize Markov state models, treating the
  configurational states of the system as a Markov process where each
  state has distinct transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation
  structure of positional fluctuations as a means of characterization and to
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative differences
  between MD and Markov state dependent model-generated trajectories may limit
  its usefulness.

  Finally, we demonstrate how one can use these models to
  estimate flux of a solute across a macroscopic-length pore and, based on
  those quantities, the membrane's selectivity towards each solute. This work
  helps to connect microscopic chemically-dependent solute motions that do not
  follow simple diffusive behavior with macroscopic membrane performance.

  }

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To all of the fluffy kitties.
	}

%  Here's where you acknowledge folks who helped. But keep it short, i.e., no more than one page,
%  as required by the Grad School Specifications.
\acknowledgements{	
  \OnePageChapter	% *MUST* BE ONLY ONE PAGE!

  I would like to acknowledge and thank a number of people whose support and
  guidance has not gone unnoticed. First, I thank my advisor, Michael Shirts, 
  who has been instrumental to my growth as a competent and confident researcher,
  pushing me to do high quality science. I thank the entire Shirts group for 
  their feedback and encouragement as well as for making our lab an enjoyable to work.
  I thank Richard Noble and Douglas Gin for their guidance on past and present 
  experimental research on LLC membranes. I also thank Michael McGrath, Gregory 
  Dwulet and Sarah Dischinger, members of the Gin and Noble groups, for providing
  invaluable experimental perspective. I thank Matthew Glaser for his 
  contributions to my understanding of liquid crystal systems. Our first paper 
  would not have been complete without his insight. I thank Joseph Yelk for his 
  effort creating the X-ray diffraction code on which our first paper relied.
  I thank Christopher Calderon for his guidance on applying Bayesian non-parametric
  techniques to solute time series.

  % BJC: should I mention the start-up? If so, I'm not sure what to say for that.
  I would like to acknowledge my financial support: The ACS Petroleum Research Fund
  grant \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN) 
  fellowship which is funded by the U.S. Department of Education.

  % BJC: This acknowledgement is how they want to be cited in papers. Could I
  % shorten it for this?
  Finally, I would like to acknowledge my high performance computing resources:
  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  }

% BJC: The list of figures and tables is obnoxious because the captions are so long.
% BJC: Can I leave them out? (would just uncomment \emptyLoF and \emptyLoT)

% \IRBprotocol{E927F29.001X}	% optional!

% \ToCisShort	% use this only for 1-page Table of Contents

% \LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

% \LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

\begin{document}

\graphicspath{{../transport/figures/}{../structure_paper/figures/}{../transport/supporting_figures/}}

\input macros.tex
\input intro.tex

\input structure.tex
%\input structure_si.tex

\input transport.tex
%\input transport_si.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{ieeetr}	% or "siam", or "alpha", etc.
%\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input structure_si.tex
\input transport_si.tex

\end{document}

### 2020-02-12 Ben_Manuscripts/thesis/transport.tex
starting dissertation

--- 2019-06-25 Ben_Manuscripts/transport/Final_Draft.tex
@@
-\documentclass[journal=jpcbfk,manuscript=article]{achemso}
-
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{amsmath} % or simply amstext
-\usepackage{amssymb}
-%\usepackage{array}
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-%\newcommand{\colormap}{jet}  % colorbar to use
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\usepackage{xr}
-\usepackage{multicol}
-\usepackage{tcolorbox}
-
-\SectionNumbersOn
-%\definecolor{amber}{rgb}{1.0, 0.75, 0.0} % amber
-%\definecolor{amber}{rgb}{1.0, 0.84, 0.0} % gold
-\definecolor{amber}{rgb}{0.99, 0.76, 0.0} % golden poppy
-
-\externaldocument[S-]{Supporting_Information}
-
-\title{Chemically Selective Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
-\author{Benjamin J. Coscia}
-\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
-\author{Michael R. Shirts}
-\email{michael.shirts@colorado.edu}
-\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
-
-\begin{document}
-
-  \graphicspath{{./figures/}}
-
-  \begin{abstract}
-
-  The uniform size and complex chemical topology of the pores formed by
-  self-assembled amphiphilic molecules such as liquid crystals make them
-  promising candidates for selective separations.
-  In this work, we observe transport of water, sodium ions and 20 small polar
-  solutes within the pores of a lyotropic liquid crystal (LLC) membrane using
-  atomistic molecular simulations. We find that the transport of a species is
-  dependent not only on molecular size, but on chemical functionality as well.
-  The membrane's inhomogeneous composition gives rise to radially dependent
-  transport mechanisms with respect to the pore centers. We observe that all
-  solutes perform intermittent hops between lengthy periods of entrapment. Three
-  different trapping mechanisms are responsible for this behavior. First, solutes
-  that drift out of the pore can become entangled among the dense monomer tails.
-  Second, solutes can donate hydrogen bonds to the monomer head groups. Third,
-  solutes can coordinate with sodium counter ions.  The degree to which a solute
-  is affected by each mechanism is dependent on the chemical functionality of the
-  solute. Using the insights developed in this study, we can begin to think about
-  how to redesign existing LLC membranes in order to perform solute-specific
-  separations.
-
-  \end{abstract}
+\chapter{Chemically Selective Transport in the H\textsubscript{II} Phase}\label{chapter:transport}
+
+  %\graphicspath{{./figs/}}
+  %\graphicspath{{/home/bcoscia/PycharmProjects/LLC_Membranes/Ben_Manuscripts/transport/figures}}
 
@@
   appropriate scripts to use for the subsequent calculations are summarized in 
-  Table~\ref{S-table:python_scripts} of the Supporting Information. We ran all 
+  Table~\ref{S-table:python_scripts_transport} of the Supporting Information. We ran all 
   MD simulations and energy minimizations using GROMACS 2018.3.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
 
-  \subsection{Molecule Parameterization}\label{method:parameterization}
+  \subsection{Molecule Parameterization}\label{method:molecule_parameterization}
 
@@
   \includegraphics[width=\textwidth]{msd_radius_ketones_10wt.pdf}
-  \caption{}\label{fig:ketones_rdf}
+  \caption{}\label{fig:ketones_msd}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{msd_radius_nondonors_10wt.pdf}
-  \caption{}\label{fig:nondonors_rdf}
+  \caption{}\label{fig:nondonors_msd}
   \end{subfigure}
@@
   that will inspire and accelerate novel design by experimentalists.
-
-  \section*{Supporting Information}
-
-  Detailed explanations and expansions upon the results and procedures mentioned in
-  the main text are described in the Supporting Information. This information is
-  available free of charge via the Internet at http://pubs.acs.org.
-
-  \section*{Acknowledgments}
-
-  B.J.C. was supported by the Graduate Assistance in Areas of National Need (GAANN) 
-  fellowship which is funded by the U.S. Department of Education.
-
-  Molecular simulations were performed using the Extreme Science and
-  Engineering Discovery Environment (XSEDE), which is supported by National
-  Science Foundation (NSF) grant number ACI-1548562. Specifically, it used the Bridges
-  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
-  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
-  which is supported by the NSF (awards ACI-1532235 and
-  ACI-1532236), the University of Colorado Boulder, and Colorado State
-  University. The Summit supercomputer is a joint effort of the University of
-  Colorado Boulder and Colorado State University.
-
-  The authors thank Christopher Calderon and Gregory Morrin for helping kick start
-  our studies of subdiffusive transport. Additionally, the authors thank 
-  Douglas Gin and Richard Noble for their guidance on past and present experimental
-  research on LLC membranes and for reading over this manuscript before submission.
-
-  \clearpage
-
-  \bibliographystyle{ieeetr}
-  \bibliography{transport}
-
-  \newpage
-
-  \section*{TOC Graphic}
-
-  \begin{figure}[!htb]
-  \centering
-  \includegraphics[width=3.25in]{toc_transport.pdf}
-  \end{figure}
-
-\end{document}
-
-% LocalWords:  lyotropic LLC solutes solute permeability micropollutants RO NF
-% LocalWords:  groundwaters flowback nanofiltration bruggen Nanostructured feng
-% LocalWords:  nanostructured mesophases Donnan Zhou al Dischinger BJC Hmm Na
-% LocalWords:  selectivities physicochemical nanopores GA pKa's protonated pKa
-% LocalWords:  gallic perrin pka NaGA MeOH URE EtOH acetamide AcN propanol PrOH
-% LocalWords:  butanol BtOH mercaptoethanol EG sulfoxide DMSO PG dimercapto DMP
-% LocalWords:  GLY tetrahydrofuran THF tetrose dimethylformamide DMF AcOH diols
-% LocalWords:  triols MSD solute's readthedocs repo GROMACS gromacs der hess wt
-% LocalWords:  Antechamber bccsym molcharge QUACPAC zhou Resel equil ca gmx COM
-% LocalWords:  solvate solvated Parrinello barostat subdiffusive superdiffusive
-% LocalWords:  subdiffusion CTRW MSDs ageing microfriction Gierer einstein Chan
-% LocalWords:  MSD's comps li Rg appoximation polson bT fr CI Luzar Chandler py
-% LocalWords:  hbonds VMD Roux genion disassociated Clauset martiniano Voloshin
-% LocalWords:  timescales binned RDFs RDF tortuosity carboxylate pdf sodium's
-% LocalWords:  mobilities timescale diffusivity msd tailvpore methanol's tamsds
-% LocalWords:  msds sublinear ztraces COMs alkane COOH HOH hbond immobilization
-% LocalWords:  counterions sulfinyl substituents electronegative COH coord na
-% LocalWords:  Carvajal Wu Shinoda carboxy ATPase rdf counterintuitively Amides
-% LocalWords:  unhindered propanol's butanol's hydrophilicity glycol's Ketones
-% LocalWords:  hybridization amides electronegativity NH ketones Thiols SOH ACI
-% LocalWords:  dimercaptoethanol dimethylsulfoxide rdfs mercaptoethanol's thiol
-% LocalWords:  formamide nondonors nanoporous XSEDE PSC RMACC TET ribose EAC
-% LocalWords:  berendsen spoel Rahman bulleted Wirtz TBD equilibrations thiols
-% LocalWords:  hbonding DMS linkable permeabilities Calderon Morrin TOC

### 2020-02-12 Ben_Manuscripts/thesis/transport_si.tex
starting dissertation

--- 2019-05-08 Ben_Manuscripts/transport/Supporting_Information.tex
@@
-\documentclass{article}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\newcommand{\colormap}{jet}  % colorbar to use
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\usepackage{xr}
+chapter{Supporting Information to Chapter 3}\label{SI:ch3}
 
-\externaldocument[M-]{Outline}
-
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thesection}{S\arabic{section}}
-\renewcommand{\thepage}{S\arabic{page}}
-\renewcommand{\thetable}{S\arabic{table}}
-
-\title{Supporting Information: Chemically Selective Transport in a Cross-linked 
-H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
-\author{Benjamin J. Coscia \and Michael R. Shirts}
-
-\begin{document}
-
-  \maketitle
-  \graphicspath{{./supporting_figures/}}
-  \bibliographystyle{ieeetr}
-
-  \section{Setup and analysis scripts}\label{section:python_scripts}
+  \section{Setup and analysis scripts}\label{S-section:python_scripts_transport}
 
@@
   Documentation for the \texttt{LLC\_Membranes} repository is available at 
-  \texttt{https://llc-membranes.readthedocs.io/en/latest/}. Table~\ref{table:python_scripts}
+  \texttt{https://llc-membranes.readthedocs.io/en/latest/}. Table~\ref{S-table:python_scripts_transport}
   provides more detail about specific scripts used for each type of analysis performed in
@@
   gives a brief description of the purpose of each script.
-  }~\label{table:python_scripts}
+  }~\label{S-table:python_scripts_transport}
 
@@
 
-  \section{Water content equilibration}\label{section:water_content_equil}
+  \section{Water content equilibration}\label{S-section:water_content_equil}
 
@@
   molecules to naturally penetrate the membrane from a water bath separating
-  periodic images of the system in the $z$-direction (see Figure~\ref{fig:gap}).
+  periodic images of the system in the $z$-direction (see Figure~\ref{S-fig:gap}).
   We allowed a dry, previously equilibrated system to further equilibrate in
@@
   times more water molecules occupy the tail region after 1000 ns of
-  equilibration (see Figure~\ref{fig:equilibrated_water_penetration}). Although
+  equilibration (see Figure~\ref{S-fig:equilibrated_water_penetration}). Although
   the water level in the pore appears to plateau in this system, it is clear that
   equilibration of this system is kinetically limited since water does not fill
-  the pores uniformly (see Figure~\ref{fig:penetration_density}). The density of
+  the pores uniformly (see Figure~\ref{S-fig:penetration_density}). The density of
   water along the pore axis, averaged over the last 50 nanoseconds of simulation,
@@
   \includegraphics[width=\linewidth]{gap.pdf}
-  \caption{}\label{fig:gap}
+  \caption{}\label{S-fig:gap}
   \end{subfigure}  
@@
   \includegraphics[width=\linewidth]{equilibrated_water_penetration.pdf}
-  \caption{}\label{fig:equilibrated_water_penetration}
+  \caption{}\label{S-fig:equilibrated_water_penetration}
   \end{subfigure}  
@@
   \includegraphics[width=\linewidth]{penetration_density.pdf}
-  \caption{}\label{fig:penetration_density}
+  \caption{}\label{S-fig:penetration_density}
   \end{subfigure}  
@@
   enters the water layer at those points.
-  }\label{fig:gap_solvation}
+  }\label{S-fig:gap_solvation}
   \end{figure}
@@
   initial pore radii of 5, 6, 7 and 8 \AA~with tail and pore water compositions
-  given in Table~\ref{table:water_content}.
+  given in Table~\ref{S-table:water_content}.
 
@@
   contents in order to study its effect on equilibrium water
-  content.}\label{table:water_content}
+  content.}\label{S-table:water_content}
   \end{table}
@@
   tails. In systems started with more water in the tails
-  (Figures~\ref{fig:r5_gap} and \ref{fig:r6_gap}), the pore water content tends
+  (Figures~\ref{S-fig:r5_gap} and \ref{S-fig:r6_gap}), the pore water content tends
   to increase over time, while that of the tails decreases or stays stable.
@@
   monomers to make space for water molecules. Systems started with a higher pore
-  water content (Figures~\ref{fig:r7_gap} and \ref{fig:r8_gap}) tend to plateau
+  water content (Figures~\ref{S-fig:r7_gap} and \ref{S-fig:r8_gap}) tend to plateau
   relatively quickly, with about one third of the water staying in the tails.  We
@@
   \includegraphics[width=\linewidth]{r5_gap.pdf}
-  \caption{r = 5~\AA}\label{fig:r5_gap}
+  \caption{r = 5~\AA}\label{S-fig:r5_gap}
   \end{subfigure}
@@
   \includegraphics[width=\linewidth]{r6_gap.pdf}
-  \caption{r = 6~\AA}\label{fig:r6_gap}
+  \caption{r = 6~\AA}\label{S-fig:r6_gap}
   \end{subfigure}
@@
   \includegraphics[width=\linewidth]{r7_gap.pdf}
-  \caption{r = 7~\AA}\label{fig:r7_gap}
+  \caption{r = 7~\AA}\label{S-fig:r7_gap}
   \end{subfigure}
@@
   \includegraphics[width=\linewidth]{r8_gap.pdf}
-  \caption{r = 8~\AA}\label{fig:r8_gap}
+  \caption{r = 8~\AA}\label{S-fig:r8_gap}
   \end{subfigure}
@@
   slow. When configurations start with more water in the pores, the water content
-  in each region equilibrates quickly.}\label{fig:gap_prefilled_equil}
+  in each region equilibrates quickly.}\label{S-fig:gap_prefilled_equil}
   \end{figure}
@@
   the total water needed in the tails, based on the intuition gained in
-  Figure~\ref{fig:gap_prefilled_equil}. We considered the water content
+  Figure~\ref{S-fig:gap_prefilled_equil}. We considered the water content
   equilibrated once the water contents plateaued. The 5 wt\% system did
-  not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
+  not plateau until $\sim$ 600 ns (Figure~\ref{S-fig:5wt_offset_equil})
   while the 10 wt \% water system equilibrated within the first 100 ns of 
-  simulation (Figure~\ref{fig:10wt_offset_equil}).
+  simulation (Figure~\ref{S-fig:10wt_offset_equil}).
   The pores contain 72 \% and 69 \% of the total water in the 5 and 10 wt \%
   systems respectively.
-
+  \clearpage
   \begin{figure}[!htb]
@@
   \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
-  \caption{5 wt \%}\label{fig:5wt_offset_equil}
+  \caption{5 wt \%}\label{S-fig:5wt_offset_equil}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
-  \caption{10 wt \%}\label{fig:10wt_offset_equil}
+  \caption{10 wt \%}\label{S-fig:10wt_offset_equil}
 % Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
@@
 	  ns, with $\sim$ 69 \% of the total water in the
-	  pores.}\label{fig:solvation_equilibration}
+	  pores.}\label{S-fig:solvation_equilibration}
   \end{figure}
@@
   \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
-  \caption{5 wt\%}\label{fig:5wt_offset_xlinked_equil}
+  \caption{5 wt\%}\label{S-fig:5wt_offset_xlinked_equil}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
-  \caption{10 wt\%}\label{fig:10wt_offset_xlinked_equil}
+  \caption{10 wt\%}\label{S-fig:10wt_offset_xlinked_equil}
 % Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
@@
   \caption{The water content in the tail and pore region is not affected
-  by cross-linking}\label{fig:solvation_equilibration}
+  by cross-linking}\label{S-fig:xlinked_solvation_equilibration}
   \end{figure}
@@
   \clearpage
-
-  \section{Solute Interaction}\label{section:solute_interaction}
+  \section{Solute Interaction}\label{S-section:solute_interaction}
 
@@
   built with 6 solutes per pore. Even methanol, which interacts with other same-solute
-  molecules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interaction}
+  molecules the most, does so less than 0.05 \% of the time.}\label{S-fig:solute_interaction}
   \end{figure}
 
-%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{section:se_sensitivity}
+%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{S-section:se_sensitivity}
 %  
@@
 %  equation with the correction factor of Gierer and Wirtz, $f$, given by 
-%  equation~\ref{M-eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
+%  equation~\ref{eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
 %  
@@
 %  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
-%  by equation~\ref{M-eqn:correction_factor} of the main text, is only applied below
+%  by equation~\ref{eqn:correction_factor} of the main text, is only applied below
 %  a critical radius. At radii greater than the critical radius, $f$ = 1.
@@
 %  to the SE equation becomes a more accurate estimation of MSD at small radii, after
-%  the point of intersection }\label{fig:se_intersection_sensitivity}
+%  the point of intersection }\label{S-fig:se_intersection_sensitivity}
 %  \end{figure}
-  \clearpage
-  \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}
+
+  \section{Solute MSD Ranking Time Lag Sensitivity}\label{S-section:lag_sensitivity}
 
   We chose to report the MSD of our solutes after a 400 ns time lag. This choice does
-  not have a significant influence on the ranking of the solute MSDs. Although there
-  is minor re-ranking among solutes with similar MSDs, it does not affect any of 
-  the conclusions drawn in the main text.
+  not have a significant influence on the ranking of the solute MSDs (see 
+  Figure~\ref{S-fig:lag_sensitivity}). Although there is minor re-ranking among solutes
+  with similar MSDs, it does not affect any of the conclusions drawn in the main text.
 
@@
   \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_2.pdf}
-  \caption{Time lag = 200 ns}\label{fig:F0.2}
+  \caption{Time lag = 200 ns}\label{S-fig:F0.2}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_3.pdf}
-  \caption{Time lag = 300 ns}\label{fig:F0.3}
+  \caption{Time lag = 300 ns}\label{S-fig:F0.3}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_4.pdf}
-  \caption{Time lag = 400 ns}\label{fig:F0.4}
+  \caption{Time lag = 400 ns}\label{S-fig:F0.4}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_5.pdf}
-  \caption{Time lag = 500 ns}\label{fig:F0.5}
+  \caption{Time lag = 500 ns}\label{S-fig:F0.5}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_6.pdf}
-  \caption{Time lag = 600 ns}\label{fig:F0.6}
+  \caption{Time lag = 600 ns}\label{S-fig:F0.6}
   \end{subfigure}
@@
   of solutes with similar MSDs and note that longer time lags generally
-  lead to large error bars on the MSDs, as expected. }\label{fig:lag_sensitivity}
+  lead to large error bars on the MSDs, as expected. }\label{S-fig:lag_sensitivity}
   \end{figure}
@@
   \clearpage
-  \section{Pore Region Definition}\label{section:pore-region}
+
+  \section{Pore Region Definition}\label{S-section:pore-region}
 
@@
   varied the cut-off in increments of 0.01 from 0.7 to 0.8 in order to
-  increase our resolution about the maximum (see Figure~\ref{fig:pore_cutoff}). 
+  increase our resolution about the maximum (see Figure~\ref{S-fig:pore_cutoff}). 
   Defining the cut-off 0.75 nm from the pore center maximizes the 
@@
 
-  \begin{figure}
+  \begin{figure}[!h]
   \centering
@@
   increments of 0.01 from 0.7 to 0.8 in order to increase our resolution
-  about the maximum.}\label{fig:pore_cutoff}
+  about the maximum.}\label{S-fig:pore_cutoff}
   \end{figure}
@@
   \clearpage
-  \section{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}
+  \section{Hydrogen Bond Detection Sensitivity}\label{S-section:hbond_sensitivity}
 
@@
   geometric criteria for hydrogen bonding. We varied the distance cut-off between 3.0 and
-  4.0 \AA, and varied the angle cut-off between 25 and 35 \degree.}\label{fig:hbond_sensitivity}
+  4.0 \AA, and varied the angle cut-off between 25 and 35 \degree.}\label{S-fig:hbond_sensitivity}
   \end{figure}
@@
   We tested the sensitivity of this criteria to ensure that our conclusions
-  were not a strong function of the chosen criteria. In Figure~\ref{fig:hbond_sensitivity} we
-  plotted the results of the same calculation performed to create Figure~\ref{M-fig:multi_hbonds}c
-  of the main text. We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
+  were not a strong function of the chosen criteria. In Figure~\ref{S-fig:hbond_sensitivity} we
+  plotted the results of the same calculation performed to create Figure~\ref{fig:multi_hbonds}c.
+  We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
   angle cut-off between 25 and 35 \degree.
@@
 
-  We can draw the same conclusions from any of the plots in Figure~\ref{fig:hbond_sensitivity}:
+  We can draw the same conclusions from any of the plots in Figure~\ref{S-fig:hbond_sensitivity}:
   \begin{enumerate}
@@
 
-  \section{Lifetime Distributions}\label{section:lifetime_distributions}
+  \section{Lifetime Distributions}\label{S-section:lifetime_distributions}
 
@@
   Example distributions generated from ethylene glycol are shown in
-  Figure~\ref{fig:lifetime_distributions}.
+  Figure~\ref{S-fig:lifetime_distributions}.
 
@@
   do not attempt to distinguish between the type of distribution and instead report
-  the 95\% confidence interval of association lifetimes.}\label{fig:lifetime_distributions}
+  the 95\% confidence interval of association lifetimes.}\label{S-fig:lifetime_distributions}
   \end{figure}
@@
   \clearpage
-  \section{Pore Splines}\label{section:splines}
+  \section{Pore Splines}\label{S-section:splines}
 
   We captured the apparent $z$-dependence of the pore center locations by
-  constructing splines running through each pore (See Figure~\ref{fig:spline}).
+  constructing splines running through each pore (See Figure~\ref{S-fig:spline}).
   Each spline consists of 10 points, equally spaced in the $z$-direction, whose
@@
   positions we defined based on the center of mass of the head groups in closest proximity
-  to the spline point in the $z$-direction.}\label{fig:spline}
+  to the spline point in the $z$-direction.}\label{S-fig:spline}
   \end{figure}
@@
 %  \clearpage
-%  \section{Total Membrane Density}\label{section:total_density}
+%  \section{Total Membrane Density}\label{S-section:total_density}
 %  BJC: moved to main text
@@
 %  that is comparable to the density in the tails far from the pore center
-%  (see figures~\ref{fig:total_density_5wt} and~\ref{fig:total_density_10wt}).
+%  (see figures~\ref{S-fig:total_density_5wt} and~\ref{S-fig:total_density_10wt}).
 %  The density is highest near the middle of the tails. The observed density distribution
@@
 %  the hexagonal phase. Accordingly, water is densest in the pore center and at 
-%  the tail ends (see figures~\ref{fig:total_water_density_5wt} 
-%  and~\ref{fig:total_water_density_10wt}). Very little water is present in the 
+%  the tail ends (see figures~\ref{S-fig:total_water_density_5wt} 
+%  and~\ref{S-fig:total_water_density_10wt}). Very little water is present in the 
 %  dense mid-tail region. 
@@
 %  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
-%  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
+%  \caption{5 wt \% water, spatial density of all atoms}\label{S-fig:total_density_5wt}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
-%  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
+%  \caption{5 wt \% water, spatial density of water}\label{S-fig:total_water_density_5wt}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
-%  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
+%  \caption{10 wt \% water, spatial density of all atoms}\label{S-fig:total_density_10wt}
 %  \end{subfigure}
@@
 %  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
-%  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
+%  \caption{10 wt \% water, spatial density of water}\label{S-fig:total_water_density_10wt}
 %  \end{subfigure}
@@
 %  tail region, furthest from the pore center (a \& c). Water is densest in the low density
-%  regions (b \& d).}\label{fig:total_density}
+%  regions (b \& d).}\label{S-fig:total_density}
 %  \end{figure}
@@
 %  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
-%  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
+%  the oxygen atom becomes associated to a different sodium ion.}\label{S-fig:na_met_trace}
 %  \end{figure}
@@
 %  \includegraphics[width=\linewidth]{SOH_trace.pdf}
-%  \caption{}\label{fig:SOH_trace}
+%  \caption{}\label{S-fig:SOH_trace}
 %  \end{subfigure}
@@
 %  After 700 ns, THF separates from the sodium ion and moves closer to the head group
-%  region.}\label{fig:thf_sodium_coordination}
+%  region.}\label{S-fig:thf_sodium_coordination}
 %  \end{figure}
@@
 %
-%  \section{Choosing a transport model}\label{section:transport_model_selection}
+%  \section{Choosing a transport model}\label{S-section:transport_model_selection}
 %
@@
 %  function of time, with $\alpha < 1$ which is indicative of anomalous
-%  subdiffusion. Figure \ref{fig:msd_power_law}a plots the ensemble-averaged MSD
+%  subdiffusion. Figure \ref{S-fig:msd_power_law}a plots the ensemble-averaged MSD
 %  curve for 24 ethanol molecules diffusing in a 10 wt\% water H\textsubscript{II}
@@
 %	  that ethanol molecules in our model exhibit subdiffusive
-%	  behavior.}\label{fig:msd_power_law}
+%	  behavior.}\label{S-fig:msd_power_law}
 %  \end{figure}
@@
 %  time-averaged and ensemble-averaged MSDs do not agree with each other
-%  (Figure~\ref{fig:ethanol_msd_comparison}). We validated our analysis using a 1
+%  (Figure~\ref{S-fig:ethanol_msd_comparison}). We validated our analysis using a 1
 %  ns simulation of a box of tip3p water molecules. As expected, since the
 %  particles exhibit Brownian motion, the time-averaged and ensemble-averaged MSDs
-%  agree with each within error (Figure~\ref{fig:water_box_msd_comparison}).
+%  agree with each within error (Figure~\ref{S-fig:water_box_msd_comparison}).
 %
@@
 %  \includegraphics[width=\textwidth]{ethanol_msd_comparison.pdf}
-%  \caption{}\label{fig:ethanol_msd_comparison}
+%  \caption{}\label{S-fig:ethanol_msd_comparison}
 %  \end{subfigure} 
@@
 %  \includegraphics[width=\textwidth]{water_box_msd_comparison.pdf}
-%  \caption{}\label{fig:water_box_msd_comparison}
+%  \caption{}\label{S-fig:water_box_msd_comparison}
 %  \end{subfigure} 
@@
 %	  (b) A box of tip3p water molecules is expected to be ergodic and it is shown to
-%	  be true here because both MSDs are in agreement. }\label{fig:msd_comparison}
+%	  be true here because both MSDs are in agreement. }\label{S-fig:msd_comparison}
 %  \end{figure}
@@
 %  autocorrelation function (ACF) of the step lengths in the $z$-direction. The
-%  ACF of a representative trajectory is shown in Figure~\ref{fig:eth_autocorrelation}.  
+%  ACF of a representative trajectory is shown in Figure~\ref{S-fig:eth_autocorrelation}.  
 %  
@@
 %	   indicating a complete loss of memory of it's previous position. Noise increases
-%	   at large time lags due to decreased sampling.}\label{fig:eth_autocorrelation}
+%	   at large time lags due to decreased sampling.}\label{S-fig:eth_autocorrelation}
 %  \end{figure}
@@
 %  \bibliography{transport}
-
-\end{document}
-
-% LocalWords:  LLC solutes py solvated GROMACS mdp solute ctrw GitHub equil xtc
-% LocalWords:  kinetically gro gmx solvate der Waals wt PR savename pl pr trr
-% LocalWords:  plateaued xlinked BJC MSDs Gierer Wirtz MSD SE tamsds hbond dist
-% LocalWords:  tetrose ribose glcyol png tortuosity nn methanol's THF ca Meroz
-% LocalWords:  Mercaptoethanol's Mercaptoethanol Complexation complexation msd
-% LocalWords:  Sokolov superdiffusion subdiffusion nojump ETH nboot RWF FBM npt
-% LocalWords:  subdiffusive CTRWs traj fracshow nanopore RW hoppy ACF brownian

### 2020-02-13 Ben_Manuscripts/thesis/intro.tex
Intro outline updates

@@
 
-  \section{Industrial Need for Highly Selective Separations}
+  \section{Membranes for Selective Separations}
 
-  \subsection{Desalination}
+  \begin{itemize}
 
-  \subsection{Separation of Organic Micropollutants}
+    \item Membranes are useful separation tools. Cover historical usage
+	\item Some discussion of competing separation technologies. 
+	\item They are more efficient and have a smaller footprint than thermal distillation.
 
-  \subsection{Recovery of Valuable Dissolved Species}
+  \end{itemize}
 
-  \subsection{Breathable Barriers}
+  \subsection{How Small Molecule Membrane Separations Work}
+
+  \begin{itemize}
+
+    \item Maybe briefly mention ultrafiltration, microfiltration
+    \item Overview of reverse osmosis and nanofiltration.
+    \item Separation mechanisms (pore flow versus solution diffusion)
+
+  \end{itemize}
+
+  \subsection{Membrane Separation Applications}
+
+  \begin{itemize}
+  	\item Desalination
+  	\item Separation of Organic Micropollutants
+  	\item Recovery of Valuable Dissolved Species
+  	\item Breathable Barriers
+  \end{itemize}
+
+  \section{Competing Membrane Technologies}
+
+  \subsection{Amorphous Membranes}
+
+  \begin{itemize}
+
+  \item Mostly about the industry standard, thin film composite polyamide membranes.
+
+  \end{itemize}
+
+  \subsection{Nanostructured Membranes}
+
+  \begin{itemize}
+
+  \item Graphene
+  \item Carbon nanotubes
+  \item zeolites
+  \item MOFs (?) %BJC: these have mostly been used for gas separations. But I've seen some work with aqueous. Not sure if worth covering.
+
+  \end{itemize}
 
@@
 
+  \begin{itemize}
+
+  \item A less studied class of membranes, LLCs, have the potential to outperform competing membranes.
+
+  \end{itemize}
+
   \subsection{The H\textsubscript{II} Phase}
+
+  \begin{itemize}
+    \item Ideal geometry for transport
+    \item Go through history
+    \item Highlight issues with synthesis
+    \item Talk about alignment approaches by Xunda Feng.
+  \end{itemize}
 
@@
 
+  \begin{itemize}
+    \item Easier to synthesize
+    \item History of monomers used
+  \end{itemize}
+
   \section{Atomistic Molecular Simulation of LLC Membranes}
+
+  \begin{itemize}
+    \item Why MD?
+    \item Why HII phase?
+    \item What work has been done already
+  \end{itemize}
+
+  Questions to be answered: %BJC: one major question per chapter
+  \begin{enumerate}
+    %\item How do we build and equilibrate these systems?
+    \item What is the nanoscopic structure?
+    \item What factors affect solute transport?
+    \item Can we estimate macroscopic properties?
+    \item How can we learn mechanisms with minimal human intervention?  %BJC: i.e. machine learning methods
+  \end{enumerate}

### 2020-02-21 Ben_Manuscripts/thesis/intro.tex
A couple of comments.
add.
Fleshing out outline

@@
 
-  \section{Membranes for Selective Separations}
+  \section{Membranes for Selective Aqueous Separations}
 
+  Pressure drive membrane processes have become an increasingly useful tool for
+  performing aqueous separations.
   \begin{itemize}
+    \item Untreated water can be a very complex solution with particles ranging
+    in size from microns down to nanometers
+    \item Sediment, bacteria, algae, proteins, small organic molecules, and ions
+    are all typical components of aqueous streams.
+%    \item Their original intention was for desalination applications but they 
+%    have since expanded their reach to a more diverse set of chemical separation
+%    problems. 
+  \end{itemize}
 
-    \item Membranes are useful separation tools. Cover historical usage
-	\item Some discussion of competing separation technologies. 
-	\item They are more efficient and have a smaller footprint than thermal distillation.
+  % BJC: This should probably go up top
+  % TFC membranes review -- "Composite reverse osmosis and nanofiltration membranes"
+  Membrane design is completely dependent on the target particle separation. 
+  \begin{itemize}
+    \item We have summarized the uses of different classes of membrane separation 
+    technologies in Figure~\ref{fig:size_regimes}
+    \item They can be classified based on the size of the particle they reject.
+    \item Microfiltration membranes contain 0.1-1.0 $\mu$m pores. (separate bacteria, pigment removal)
+    \item Ultrafiltration (sugars, proteins, colloidal materials) pore size about 0.05 $\mu$m
+    \item Nanofiltration have pores on the order of 1 nm in size
+    \item Reverse osmosis membranes are dense amorphous polymers with no explicit pores
+    \item These technologies are often used in series
+  \end{itemize}
 
-  \end{itemize}
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/membrane_separation_size_regimes.pdf}
+  \caption{}\label{fig:size_regimes}
+  \end{figure}
 
@@
 
+  %\wijmans_solution-diffusion_1995
+  Membrane permeation is the result of a chemical potential gradient $\frac{d\mu_i}{dx}$.
   \begin{itemize}
+	  \item The flux of component $i$ is proportional to this gradient:
+	  \begin{equation}
+	    J_i = -L_i \frac{d\mu_i}{dx}
+	  \end{equation}
+	  where $L_i$ is a coefficient of proportionality.
+	  \item Chemical potential gradients can be induced by concentration, pressure, 
+	  temperature and electromotive force.
+  \end{itemize}
 
-    \item Maybe briefly mention ultrafiltration, microfiltration
-    \item Overview of reverse osmosis and nanofiltration.
-    \item Separation mechanisms (pore flow versus solution diffusion)
+  % This follows the discussion of werber_material_2016
+  For pressure driven membrane processes, water flux through both porous and 
+  amorphous membranes can be described by
+  \begin{equation}
+  J_w = A(\Delta P - \Delta \pi_m)
+  \end{equation}
+  where $J_w$ is volumetric water flux, $A$ is the water permeability coefficient,
+  $\Delta P$ is the applied hydraulic pressure and $\Delta \pi_m$ is the 
+  trans-membrane osmotic pressure difference. The water permeability coefficient
+  is dependent on how one models flow through the membrane.
 
+  In porous membrane architectures, water flux is modeled as laminar flow through 
+  cylindrical pores.
+  \begin{itemize}
+    \item The derivation follows Hagen-Poiseuille flow with inclusion of morphological
+    characteristics:
+    \begin{equation}
+    A = \frac{\varepsilon r_p^2}{8\mu\delta_m}
+    \end{equation}
+    where $\varepsilon$ is the surface porosity, $r_p$ the pore radius, $\delta_m$ the
+    membrane thickness, and $\mu$ the solution viscosity.
+    \item Separation is considered in terms of rejection. Solutes with radii smaller
+    than the pore will be rejected. A distribution of pore sizes prevents perfect
+    rejection.
   \end{itemize}
+
+  In amorphous membranes, water flux is modeled using the solution-diffusion 
+  model.
+  \begin{itemize}
+    \item It is hypothesized that water and solute molecules partition into the
+    membrane and diffuse across the polymer matrix due to a chemical potential
+    gradient and then desorb into the permeate.
+    \item The solubility and diffusivity can be described  in terms of the 
+    diffusive water and solute permeabilities ($P_w$ and $P_s$) respectively
+    \item \begin{equation}
+    A = \frac{P_wV_w}{\delta_mR_gT}
+    \end{equation}
+    where $V_w$ is molar volume of water, $R_g$ is the gas constant and $T$ is
+    absolute temperature.
+    \item Solute flux is modeled as:
+    \begin{equation}
+    J_s = \frac{P_s}{\delta_m}\Delta c_m
+    \end{equation}
+  \end{itemize}
+
+  These equations provide a somewhat limited perspective on the molecular details
+  of transport.
 
@@
 
+  Selective separations are useful for a wide range of applications.
+
+  % Put this with the desalination section below maybe
+  % morton_environmental_1996,bhojwani_technology_2019
+  \textit{Desalination}:
+  Creating potable water from seawater or brackish water is of paramount importance
+  in water-scarce areas. 
   \begin{itemize}
-  	\item Desalination
-  	\item Separation of Organic Micropollutants
-  	\item Recovery of Valuable Dissolved Species
-  	\item Breathable Barriers
+  	\item Compared with thermal distillation techniques, reverse osmosis has been 
+  	shown to be more environmently friendly and economical due to its lower energy
+  	requirements.
+  	\item Thermal techniques are still preferred where excess waste heat or cheap 
+  	thermal energy is available, such as cogeneration plants.
+  	\item RO has smaller footprint?
+  \end{itemize}
+
+  \textit{Organic Micropollutants}:
+  Municipal and industrial wastewaters are contaminated by harmful
+  micropollutants, which have adverse effects on human health even at low 
+  concentrations\cite{schwarzenbach_challenge_2006}
+  \begin{itemize}
+    \item Micropollutants include pharmaceutical and personal care products, 
+    hormones, pesticides and industrial chemicals which find their way into
+    our drinking water supply
+    \item Is there any infrastructure built to combat this?
+  \end{itemize}
+
+  \textit{Recovery of Valuable Dissolved Species}: We can use highly selective
+  membranes in order to recover potentially valueable dissolved species from 
+  complex waste streams.
+
+  Municipal waste-waters are rich in carbon, nitrogen and phosphorus-containing 
+  compounds. 
+  \begin{itemize}  
+    \item The recovery of such products, which can be achieved using a 
+    selective membrane, has numerous potential uses.\cite{sales_resource_2015}
+    \item For example, nitrogen and phosphorus recovery can help sustain fertilizer 
+    production which will help meet global food demand as population continues
+    to increase.\cite{xie_membrane-based_2016}
+  \end{itemize}
+
+  Industrial waste-waters are often quite complex with up to six times more 
+  total dissolved solids than seawater\cite{werber_materials_2016}. 
+  \begin{itemize}
+    \item For example, flowback water, produced during hydraulic fracturing of
+    shale formations consists of relatively high concentrations of salts, metals,
+    and soluble organic compounds. 
+    \item The majority of this water is disposed through deep well injection, 
+    however there is a growing public concern about its management which has 
+    prompted the use of separation technologies such as RO and NF in order to 
+    reduce the volume of contaminated water~\cite{gregory_water_2011}.
+    \item Some of the dissolved organic compounds in flowback water, such as acetate, 
+    are potentially valuable and can be recovered with highly selective membranes
+    \cite{dischinger_application_2017}.
+  \end{itemize}
+
+  \textit{Breathable barriers}:
+  Finally, there is a great deal of military interest in creating breathable 
+  barriers which selectively allow the passage of water in both directions but
+  blocks out harmful contaminants.
+  \begin{itemize}
+    \item Need to allow sweating
+    \item Can even put catalytic groups in the pores to break down contaminants
   \end{itemize}
@@
 
+  Amorphous thin film composite (TFC) RO membranes are the current industry standard for
+  high purity separations.
   \begin{itemize}  
+    \item Mostly desalination (?)
+    \item Typically you have a porous support layer for mechanical strength and 
+    very thin active layer where the separations occur.
+    \item Usually only let water through. Usually have to remineralize the
+    water to make it drinkable.
+  \end{itemize}
 
-  \item Mostly about the industry standard, thin film composite polyamide membranes.
+  Operation requires high feed pressures.
 
+  \subsection{Standard Nanofiltration}
+
+  Unlike RO membranes, NF membranes have explicitly defined pores. An
+  ideal NF membrane should have densely packed, uniform-sized and
+  non-tortuous pores. This combination has been very difficult to realize.
+
+  NF membranes are typically made by a phase-inversion process. The most 
+  widely used phase-inversion process is immersion precipitation.
+  \begin{itemize}
+    \item During which one submerges a polymer, dissolved in a solvent, in
+    a non-solvent.
+    \item A solid, porous polymer membrane is all that remains once all
+    solvent has been removed by non-solvent exchange \cite{smolders_microstructures_1992}.
+    \item The resultant pores are polydisperse in size, which hurts membrane selectivity. 
   \end{itemize}
+
+  A second technique used to create NF membranes is call track-etching in which a polymer
+  film is bombarded with charged particles, then chemically etched to create pores
+  \cite{apel_track_2001}. The pores are uniform, which benefits selectivity;
+  however, the membranes have a low porosity and subsequently low permeability.
+
+  Explicitly defined pores allows much lower feed pressures. However, polydispersity in
+  pore size lowers their selectivity relative to RO.
 
@@
 
+  Nanostructured membrane materials have the potential to achieve the high selectivity
+  of RO with the low feed pressure requirements of NF. Nanostructured materials of 
+  interest typically have explicit nm-size pores that are uniform in size, eliminating
+  issues with polydispersity. There have been a number explorations into different
+  kinds of technologies for this application.
+
+  %BJC: format for following paragraphs maybe: Introduce tech, say how it would work, why it doesn't work 
+  Ultrathin-film
+  graphene and graphene oxide membranes are an active area of research because
+  they are atomically thick and therefore offer potential for extremely high
+  permeability membranes.~\cite{humplik_nanostructured_2011} 
   \begin{itemize}  
+    \item However, scalable synthesis without introducing microscopic, performance
+    degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
+  \end{itemize}
 
-  \item Graphene
-  \item Carbon nanotubes
-  \item zeolites
-  \item MOFs (?) %BJC: these have mostly been used for gas separations. But I've seen some work with aqueous. Not sure if worth covering.
+  Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
+  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001}
+  \begin{itemize}
+	\item Practically, dispersing and aligning CNTs into a polymer matrix is extremely
+    difficult because they tend to agglomerate due to Van der Waals forces.~\cite{sahoo_polymer_2010}
+    \item Some work has been to functionalize the carbon nanotubes in order to better incorporate them. % need reference
+  \end{itemize}
 
+  Zeolite-coated ceramic membranes offer the potential for permeabilities
+  comparable to ultrafiltration, with selectivities as good as NF and RO.%BJC: werber a possible reference?
+  \begin{itemize}
+	\item A number of studies have tested the permeability and sodium salt rejection
+    of various zeolite membranes, however none have fully overcome the
+    permeability-selectivity tradeoff.~\cite{pendergast_review_2011,auerbach_handbook_2003,li_novel_2007}
+  \end{itemize}
+
+  Finally, metal organic frameworks (MOFs) have been recently introduced to the
+  field of aqueous separations.
+  \begin{itemize}
+    \item They were orginally used for gas separations
   \end{itemize}
@@
 
+  Under the right conditions, the shape and amphiphilic character of the monomers in 
+  Figure TBD drives their self assembly into ordered nanostructures.
   \begin{itemize}
-
-  \item A less studied class of membranes, LLCs, have the potential to outperform competing membranes.
-
+    \item Monomer 1 can form the inverted hexagonal phase (H\textsubscript{II})
+    \item Monomer 2 will form the bicontinuous cubic phase (Q\textsubscript{I})
+    \item The tails have vinyl groups which can be cross-linked for mechanical strength.
   \end{itemize}
 
+  %BJC: figure here showing each monomer and the phase they form
+
+  In this work we study LLC membranes as an alternative nanostructured material for 
+  highly selective aqueous separations.
+
   \subsection{The H\textsubscript{II} Phase}
+
+  The H\textsubscript{II} phase is characterized by hexagonally packed, uniform-sized
+  and straight pores.
+  \begin{itemize}
+    \item The hydrophilic head groups aggregate in the pore centers to create
+    cylindrical aqueous channels. 
+    \item These pore channels are lined with the chemical functionality of the LLC monomers
+    and have the potential to interact with solutes in a chemically-dependent manner.
+    \item In theory, this topology is ideal for high flux and highly selective separations.
+  \end{itemize}
+
+  Unfortunately, it is a difficult task to align the self-assembled hexagonal
+  mesophases into continuous pores that traverse the width of the membrane.
+  \begin{itemize}
+    \item Although the membranes have shown high experimental selectivity, their 
+    flux has been very low due to misalignment of the hexagonal mesophases.
+    \item There has been 
+  \end{itemize}
 
@@
     %\item How do we build and equilibrate these systems? 
-    \item What is the nanoscopic structure?
-    \item What factors affect solute transport?
+    \item What is the nanoscopic structure?  %MRS: good instinct to focus on this one. Build and equilibrate is a 'how' that allows you to get at this more important question.  
+    \item What factors affect solute transport?  %MRS: make ``factors'' more specific and physical.
     \item Can we estimate macroscopic properties?

### 2020-02-26 Ben_Manuscripts/thesis/intro.tex
Beefing up outline

@@
 
-  \section{Membranes for Selective Aqueous Separations}
+  \section{Membranes for Aqueous Separations}
 
-  Pressure drive membrane processes have become an increasingly useful tool for
+  %BJC: limiting to pressure driven aqueous membrane separations (so I don't have to get into electrodialysis, gas separations, dialysis etc.)
+  Pressure driven membrane processes have become an increasingly useful tool for
   performing aqueous separations.
@@
     \item Sediment, bacteria, algae, proteins, small organic molecules, and ions
-    are all typical components of aqueous streams.
-%    \item Their original intention was for desalination applications but they 
-%    have since expanded their reach to a more diverse set of chemical separation
-%    problems. 
+    are all common components of aqueous streams.
   \end{itemize}
 
-  % BJC: This should probably go up top
   % TFC membranes review -- "Composite reverse osmosis and nanofiltration membranes"
-  Membrane design is completely dependent on the target particle separation. 
+  \noindent Membrane design is completely dependent on the target particle separation. 
   \begin{itemize}
-    \item We have summarized the uses of different classes of membrane separation 
-    technologies in Figure~\ref{fig:size_regimes}
     \item They can be classified based on the size of the particle they reject.
-    \item Microfiltration membranes contain 0.1-1.0 $\mu$m pores. (separate bacteria, pigment removal)
-    \item Ultrafiltration (sugars, proteins, colloidal materials) pore size about 0.05 $\mu$m
-    \item Nanofiltration have pores on the order of 1 nm in size
-    \item Reverse osmosis membranes are dense amorphous polymers with no explicit pores
-    \item These technologies are often used in series
+    \item Microfiltration membranes contain 100-10000 nm pores. They can separate large
+    particles like bacteria and protozoa.~\cite{ma_functionalized_2014}
+    \item Ultrafiltration membranes have pore sizes about 5-500 nm and are useful for the 
+    separation of sugars, proteins, viruses and colloidal materials.~\cite{davey_ultrafiltration_2009}
+    \item Nanofiltration have pores on the order of 1 nm in size and can be used for the separation
+    of small organic molecules and charged species.~\cite{van_der_bruggen_review_2003}
+    \item Reverse osmosis membranes are dense amorphous polymers with no explicit pores. Their
+    dense polymer architecture reject all solutes except water making them useful for 
+    separating hydrated ions from water.~\cite{warsinger_review_2018}
+    \item We have summarized the uses of different classes of membrane 
+    technologies in Figure~\ref{fig:size_regimes}.
+    \item To deal with complex aqueous streams, and to prevent excessive membrane fouling, 
+    these technologies are often used in series, removing larger particles first.~\cite{goosen_fouling_2005}
   \end{itemize}
@@
 
-  \subsection{How Small Molecule Membrane Separations Work}
-
-  %\wijmans_solution-diffusion_1995
-  Membrane permeation is the result of a chemical potential gradient $\frac{d\mu_i}{dx}$.
+  \noindent Membrane permeation is the result of a chemical potential gradient, $\frac{d\mu_i}{dx}$.
   \begin{itemize}
@@
 	  \end{equation}
-	  where $L_i$ is a coefficient of proportionality.
+	  where $L_i$ is a coefficient of proportionality.~\cite{wijmans_solution-diffusion_1995}
 	  \item Chemical potential gradients can be induced by concentration, pressure, 
-	  temperature and electromotive force.
+	  temperature and electromotive forces.
+	  \item We will limit our discussion to concentration and pressure gradients.
   \end{itemize}
@@
     membrane thickness, and $\mu$ the solution viscosity.
-    \item Separation is considered in terms of rejection. Solutes with radii smaller
-    than the pore will be rejected. A distribution of pore sizes prevents perfect
-    rejection.
+    \item Separation is typically characterized in terms of solute rejection, $R$. 
+    \begin{equation}
+      R = 1 - \frac{c_p}{c_f}
+    \end{equation}
+    where $c_p$ and $c_f$ are the concentrations of the rejected species in
+    the permeate and feed respectively.
+    \item Solutes with radii smaller than the pore will be rejected. A distribution of 
+    pore sizes prevents perfect rejection.
   \end{itemize}
 
-  In amorphous membranes, water flux is modeled using the solution-diffusion 
+  \noindent In amorphous membranes, water flux is modeled using the solution-diffusion 
   model.
@@
     \begin{equation}
-    J_s = \frac{P_s}{\delta_m}\Delta c_m
+    J_s = \frac{P_s}{\delta_m}\Delta c_m = B\Delta c_m
     \end{equation}
+    where B is a solute permeability coefficient and \Delta c_m is the concentration
+    difference across the selective membrane layer.
+    \item Under these assumptions, rejection can be reformulated as
+    \begin{equation}
+    R = \frac{A}{A + B}
+    \end{equation}
+    which approaches unity as the solute flux tends towards zero.
   \end{itemize}
 
-  These equations provide a somewhat limited perspective on the molecular details
-  of transport.
+  Although there has been considerable focus on creating membranes with high
+  permeabilities, there is a case to be made that shifting the focus to membrane
+  selectivity may offer a more effective route towards lowering the cost of 
+  membrane separations.
+  \begin{itemize}
+    \item Increasing permeabilities beyond those already achieved may have 
+    only a small effect on energy requirements and capital costs. 
+    \item Cohen-Tanugi et al. calculated that tripling membrane permeability
+    could reduce energy consumption up to 15\% in a seawater reverse osmosis plant.~\cite{cohen-tanugi_quantifying_2014}
+    \item Perhaps the biggest detriment to energy consumption is the practical
+	need for multiple membrane passes in order to achieve a desired purity.
+    \item Additionally, many membranes are not suited for high purity separations
+    of small neutral species which requires chemical and capital costs for
+    post-treatment
+    \item Addressing these problems with highly selective separations may lead to 
+    more gains.
+  \end{itemize}
 
-  \subsection{Membrane Separation Applications}
+%  These equations provide a somewhat limited perspective on the molecular details
+%  of transport.
+%  \begin{itemize}
+%    \item The parameters are experimental observables which allow one to 
+%    speculate on the atomic-level 
+%  \end{itemize}
+
+  \subsection{Applications of Selective Membranes}
 
@@
     flux has been very low due to misalignment of the hexagonal mesophases.
-    \item There has been 
   \end{itemize}
 
+%  Recently, Feng et al. has come up with two methods which can be used to 
+%  macroscopically align the hexagonal mesophases. 
+  Considerable recent efforts have made progress towards the macroscopic
+  alignment of the hexagonal mesophases.
   \begin{itemize}
-    \item Ideal geometry for transport
-    \item Go through history
-    \item Highlight issues with synthesis
-    \item Talk about alignment approaches by Xunda Feng.
+    \item Feng et al. leverage the magnetic anisotropy of the columnar \
+    mesophases in order to control their alignment with a magnetic field~\cite{feng_scalable_2014}
+    \item Feng et al. also used an approach caused soft confinement which
+    takes advantage of the hexagonal columns preference towards anchoring
+    perpendicular to either a PDMS or glass substrate.~\cite{feng_thin_2016}
+    \item Finally, Feng et al. designed a third technique which uses a structure
+    directing molecule in order to template the assembly of a fatty acid 
+    molecule into ordered columnar phases.~\cite{feng_highly_2017}
   \end{itemize}
@@
 
+  The bicontinuous cubic, or Q\textsubscript{I} phase, is a class 
+  of nanostructured phases characterized by 3D interconnected pores.
   \begin{itemize}
-    \item Easier to synthesize
-    \item History of monomers used
+    \item Aside from its tortuous pore architecture, it shares the 
+    uniform size and complex topological features of the H\textsubscript{II} phase
+    which lends itself to highly selective separations.
+    \item Although water and solutes must follow a longer path in order to pass
+    through Q\textsubscript{I} membranes, they are more practical to synthesize
+    because the mesophases do not require alignment. 
+  \end{itemize}
+
+  The space group of the Q\textsubscript{I} phase configuration formed by
+  monomer 1 is uncertain and thought to be either Pn3m or Ia3d.
+  \begin{itemize}
+    \item 6 Q phase architectures have been identified in small molecule
+    amphiphile systems.~\cite{mariani_cubic_1988}
+    \item Of these, only 4 are consistent with diffraction data generated
+    by the gemini surfactant used here.~\cite{pindzola_cross-linked_2003}
+    \item Q$^{230}$ (Ia3d), Q$^{224}$ (Pn3m), Q$^{229}$ (Im3m) or Q$^{212}$ (P4\textsubscript{3}32) phase of type I configuration
+    \item The presence of $1 / \sqrt{6}$ and $1 / \sqrt{8}$ peaks rules out the
+    Q$^{227}$ (Fd3m) and Q$^{223}$ (Pm3n) configurations.
+    \item The Pn3m and Ia3d architectures are the most common~\cite{mariani_cubic_1988,wiesenauer_nanoporous_2012}
+    \item The most likely phase is the type I Q$^{230}$ (Ia3d) because it is the
+    most common phase observed between lamellar and hexagonal phases and the
+    monomeric alkyltrimethylammonium salts used to synthesize the gemini LCs
+    exhibit clear Ia3d symmetry.
+  \end{itemize}
+
+  Due to its more facile synthesis, there has been significantly more development
+  of Q\textsubscript{I} phase-forming monomers.
+  \begin{itemize}
+    \item The first generation of Q\textsubscript{I} membranes was made by 
+    the self-assembly of a gemini phosphonium monomer in water.~\cite{pindzola_cross-linked_2003}
+    \item Hatakeyama et al. improved the industrial viability of Q\textsubscript{I} 
+    phase membranes by using a gemini ammonium monomer which is both easier and cheaper
+    to synthesize.~\cite{hatakeyama_nanoporous_2010}
+    \item Free standing films of both first and second generation Q\textsubscript{I} phase 
+    membranes cannot withstand high pressure. Because solution casting was ineffective, Zhou
+    et. al used a hot-pressing method to make mechanically strong membranes which involves 
+    heating the initial monomer mixture to 70\degree C and pressing it with 12 tons of force
+    into a thick microporous, hydrophilic polymer support.~\cite{zhou_new_2007}
+    \item The most recent generation of Q\textsubscript{I} membranes uses an imidazolium-based
+    gemini LLC monomer which is capable of being solution cast into defect-free thin films on
+    porous supports. This improvement resulted in a ten-fold increase in flux while retaining
+    selectivities similar to earlier generations.~\cite{carter_glycerol-based_2012}
+  \end{itemize}
+
+  %BJC: figure with different generation Q1 monomers
+
+  State of the art Q\textsubscript{I} membranes offer selectivities that
+  are competitive with existing commercial technologies.
+  \begin{itemize}
+    \item When separating organic solutes from NaCl, Q\textsubscript{I}-phase
+    membrane filtration experiments have shown selectivity 2--3 times higher than
+    commercial RO and 6--12 times higher than commercial NF membranes
+    \cite{dischinger_application_2017}.
+    \item Water permeability is higher than commercial RO membranes but
+    less than commercial NF. There is work being done to reduce the
+    thickness of the selective layer in order to increase permeability. 
   \end{itemize}
@@
 
+  %BJC: following two paragraphs taken from first paper.
+  Our current understanding of the molecular details of LLC polymer membranes'
+  nanostructure is not sufficient to be able to precisely design them for
+  specific separations. Dischinger et al.~attempted to use an empirical model
+  that correlates the physiochemical properties of the counterion used in a
+  Q\textsubscript{I}-phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
+  Although their model showed some qualitative agreement with experiment, the
+  quality of fit of their model was limited due to complex solute-membrane
+  interactions that could not easily be modeled. Additionally, they observed
+  an unexpected discrepancy in the relationship between uncharged solute
+  rejection and water permeability, which will require a more in-depth knowledge of
+  the difference between solute and solvent transport.
+
+  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane
+  studies have been limited primarily to the Na-GA3C11 monomer with some
+  characterization done after minor structural modifications. For example, Resel
+  et al.~varied the length of the monomer tails and the counterion used and
+  observed its effect on pore spacing \cite{resel_structural_2000}. In a later
+  study of rejection performance, it was shown that membranes formed by
+  cross-linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes
+  less than 1.2 nm in diameter because the pores are too large
+  \cite{zhou_supported_2005}. We do not yet understand how to controllably reduce
+  the effective pore size or how to tune the chemical environment in the
+  nanopores of this or related materials for small molecule separations. The only
+  source of predictive modeling for LLC systems have been macroscopic models that
+  likely do not adequately describe transport at these length scales
+  \cite{hatakeyama_water_2011}. Modeling with molecular detail could provide
+  sufficient information about the mechanisms and chemical features to better
+  inform experimental design of similar nanostructured membranes.
+
+  A molecular-level understanding of the relationship between monomer structure
+  and solute transport can help provide guidelines to reduce the
+  large chemical space available to design monomers for creation of
+  separation-specific membranes.
   \begin{itemize}
-    \item Why MD?
-    \item Why HII phase?
-    \item What work has been done already
+    \item Atomistic MD simulations can provide the required level of detail 
+    (Figure \ref{fig:detailed_pore}), assuming the force fields are sufficiently accurate. 
+    \item With such an atomistic model, we can directly observe
+  molecular-level solute transport and suggest governing mechanisms. 
+    \item We can also observe how the choice of head group interacts with solutes
+    of interest. 
+    \item In addition, we can interchange counterions which may influence both the pore size
+    and the strength of the Donnan potential.
   \end{itemize}
 
-  Questions to be answered: %BJC: one major question per chapter
+  \begin{figure}[!htb]
+  \centering
+	\begin{subfigure}{0.45\linewidth}
+		\centering
+		\includegraphics[width=0.6\textwidth]{cartoon_pore.pdf}
+		\caption{}~\label{fig:undetailed_pore}
+	\end{subfigure}
+	\begin{subfigure}{0.45\linewidth}
+		\centering
+		\includegraphics[width=0.6\textwidth]{detailed_pore.pdf}
+		\caption{}~\label{fig:detailed_pore}
+	\end{subfigure} 
+    \caption{(a) Previous understanding of the LLC pores are essentially speculations 
+    based on limited chemical and experimental data. (b) We use detailed molecular 
+    modeling in this paper in order to appropriately model the pore's complex architecture,
+    which is crucial to understanding the mechanism of solute transport. In both 
+    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
+  \end{figure}
+
+  Although the Q\textsubscript{I} phase shows the most promise for
+  practical applications, the focus of this work will be on the H\textsubscript{II}
+  phase.
+  \begin{itemize}
+    \item The H\textsubscript{II} phase is an easier to geometry to model
+    and analyze.
+    \item We also have detailed structural data which is necessary for validating
+    our model.
+    \item All of the analysis techniques we use can be equally adapted to
+    the more complicated Q\textsubscript{I} phase geometry.
+  \end{itemize}
+
+  There are few molecular simulation studies which study structure and transport
+  in LLC systems.
+  \begin{itemize}
+    \item Mondal et al. used MD simulations to study the self assembly of gemini 
+    surfactants and observed the formation of H\textsubscript{II} and Q\textsubscript{I}
+    phases depending on water content.\cite{mondal_self-assembly_2013}
+    \item Mantha and Yethiraj as well as Roy et al. studied the dynamics of confined 
+    water in these systems and showed orders of magnitude differences in their motion
+    dependent on system geometry.~\cite{mantha_dynamics_2016,roy_water_2016}
+    \item Jackson et al. as well as Manthan et al. have combined experiment with simulation
+    in order to show how the choice of monomer head group counterion regulate water 
+    dynamics.~\cite{jackson_ion-specific_2018,mantha_counterion-regulated_2018}
+    \item Sakamoto et al. and Nada et al. observed the dynamics of water molecules
+    and ions and hypothesized transport mechanisms in a simplified model of an LLC
+    nanopore.~\cite{sakamoto_development_2018,nada_transport_2020}
+  \end{itemize}
+
+  Because there is relatively sparse coverage of these types of simulation systems in 
+  the literature, we have built a detailed molecular model from the ground up. There 
+  are four primary research questions that we will address in this work.
   \begin{enumerate}
-    %\item How do we build and equilibrate these systems? 
-    \item What is the nanoscopic structure?  %MRS: good instinct to focus on this one. Build and equilibrate is a 'how' that allows you to get at this more important question.  
-    \item What factors affect solute transport?  %MRS: make ``factors'' more specific and physical.
-    \item Can we estimate macroscopic properties?
+    \item What is the nanoscopic structure?
+    	\begin{itemize}
+    	  \item Before we can try to understand the molecular mechanisms of solute
+    	  transport, we need to ensure that we model the chemical environment
+    	  within the nanopores in a way that is consistent with experiment.
+    	  \item We use experimental structural data in order to validate our model.
+    	\end{itemize}
+    \item Which solute-membrane interactions have the greatest influence on transport rates?
+    	\begin{itemize}
+    	  \item After gaining a detailed picture of the nanopore structure, we can 
+    	  feel confident that solutes in this system will experience the same 
+    	  interactions which are present in a real system.
+    	  \item We create independent systems for each of 20 small polar solutes 
+    	  and observe transport mechanisms whose dominance is dependent on
+    	  solute chemical functionality.
+    	  \item We characterize three different trapping mechanisms which lead
+    	  to subdiffusive transport behavior.
+    	\end{itemize}
+    \item Can we estimate experimentally-relevant macroscopic properties?
+    	\begin{itemize}
+    	  \item Using our qualitative understanding of the dominant trapping mechanisms,
+    	  we develop stochastic time series models which we can use to mimic solute dynamic
+    	  behavior on time scales orders of magnitude longer than our simulations. 
+    	  \item We attempt to reproduce both quantitative and qualitative solute trajectory
+    	  behavior on MD simulation-length timescales.
+    	  \item We then show how we can use our most promsiing model in order to connect 
+    	  microscopic transport to macroscopic flux and selectivity.
+    	\end{itemize}
     \item How can we learn mechanisms with minimal human intervention?  %BJC: i.e. machine learning methods
+    	\begin{itemize}
+    	  \item Although our stochastic models show great promise, their development 
+    	  require some qualitative and quantitative understanding of dominant transport
+    	  mechanisms.
+    	  \item In the final chapter, we use the infinite hidden Markov model in order
+    	  to automatically detect and parameterize a unknown number of hidden dynamical modes
+    	  exhibited by solute time series. 
+    	  \item This more flexible approach allows us to both infer mechanisms based 
+    	  on differences in dynamical behavior and generate stochastic trajectory realizations
+    	  which we can use to predict flux and selectivity. 
+    	\end{itemize}
   \end{enumerate}

### 2020-02-27 Ben_Manuscripts/hdphmm/Outline.tex
A few comments.
More implementation details and background

@@
 
-%Predicting Flux and Selectivity of Solutes in a Nanostructured Membrane using the Infinite Hidden Markov Model
-\title{Stochastic Models Parameterized by the Infinite Hidden Markov Model Can Predict Flux and Selectivity of Solutes in Nanostructured Membranes.}
+\title{Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
+       of Solute Trajectories in Nanostructured Membranes.}
 
-\author{Benjamin J. Coscia, Chris Calderon \and Michael R. Shirts}
+\author{Benjamin J. Coscia, Christopher P. Calderon \and Michael R. Shirts}
 
@@
 
-  We need highly selective membranes in order to perform efficient separations. \\
+  There is a need for highly selective membranes in order to perform efficient 
+  separations of components of complex aqueous streams.
+  \begin{itemize}
+    \item Organic micropollutants
+    \item Desalination and boric acid removal from seawater.
+    \item While many researchers focus on membrane permeability, we may be 
+    able to reduce costs of commercial nanofiltration and reverse osmosis with
+    higher selectivity.~\cite{werber_materials_2016}
+  \end{itemize}
 
-  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.\\
-
-  Lyotropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
-  into mechanically strong membranes.\\
+%  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.
 %  \begin{itemize}
-%  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
-%	sized pores and have the potential to disrupt conventional membrane separation
-%	techniques by being selective based not only on size and charge, but on chemical
-%	functionality as well.
-%	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
-%	pores. They are easier to make.
+%    \item 
 %  \end{itemize}
 
-  We can only learn so much from experiment. MD can give us mechanistic insights with
-  atomistic resolution so that we can intelligently design new membranes for 
-  solute-specific separations.\\
+  Lyotropic liquid crystals (LLC) are a class of amphiphilic molecules whose ordered phases
+  can be cross-linked into mechanically strong membranes capable of highly selective
+  separations.
+  \begin{itemize}
+    \item The shape of the LLC monomers and water content dictates the ordered phase 
+    that they form. There are two phases of particular interest for membrane applications.
+  	\item H\textsubscript{II} phase lyotropic liquid crystals are characterized by 
+  	hexagonally packed, straight, pores while the Q\textsubscript{I} phase consists of
+  	a tortuous network of 3D interconnected pores. 
+  	\item In both cases the pores are uniform in size with radii on the order of 1 nm
+  	giving them a very strict molecular weight cut-off.
+	\item Additionally, they have the potential to disrupt conventional membrane separation
+	techniques by being selective based not only on size and charge, but on chemical
+	functionality as well.
+	\item Their pores are lined with LLC monomer functional groups which can potentially
+	be designed to interact with solutes in a chemically-specific manner
+  \end{itemize}
+
+  There are limits to what we can learn from experiment about LLC membrane design.
+  \begin{itemize}
+    \item Experimental observables like permeability and selectivity allow us to speculate
+    about the molecular origins of separation processes.
+    \item This drives an empirical design approach which can potentially neglect key
+    interactions which influence selectivity.
+    \item LLC membranes have been shown to exhibit selectivities which cannot be fully 
+    explained by relatively simple macroscopic models. 
+  \end{itemize}
+
+  Molecular Dynamics (MD) simulations can give us mechanistic insights with atomistic 
+  resolution so that we can intelligently design new membranes for solute-specific 
+  separations.
+  \begin{itemize}
+    \item In our previous work, we built a detailed atomistic model which we used
+    to understand the nanoscopic structure of an LLC Membrane.~\cite{coscia_understanding_2019}
+    \item We also used the model in order to gain a qualitative understanding of 
+    trapping mechanisms which lead to subdiffusive transport behavior.~\cite{coscia_chemically_2019}
+  \end{itemize}
 
@@
   \begin{itemize}
-  	\item Brief description of anomalous diffusion
-  	\item Brief description of MSDDM
+  	\item In our first approach we modeled solute trajectories as subordinated fractional
+  	Brownian and L\'evy motion, called the anomalous diffusion (AD) model. 
+  	\item We generated solute trajectories by generating a series
+  	of anti-correlated hops separated by random periods of entrapment drawn from a 
+  	power law distribution.
+  	\item Our second approach treated solute motion as a Markov state model with
+  	state-dependent dynamics, called the Markov state-dependent dynamical model (MSDDM).
+  	\item We parameterized the state transition probabilities between
+  	each of eight discrete states as well as the solute dynamics within each of these
+  	states. We generated stochastic trajectory realizations by drawing a state
+  	sequence based on the transition probability matrix and incorporating the state dynamics
+  	while solutes were trapped in each state.
+%  	\item Both models had moderate success reproducing the mean squared displacements (MSDs)
+%  	exhibited by solutes in our MD simulations.
   \end{itemize}
 
-  Although both models had reasonable success at predicting solute MSDs on simulation
-  timescales, they had shortcomings.
+  Although both models had reasonable success at predicting solute mean squared 
+  displacements (MSDs) on MD simulation timescales, they had shortcomings.
   \begin{itemize}
-  	\item Why MSDDM failed
-  	\item Why anomalous diffusion model could be better.
+  	\item The MSDDM failed to reproduce the hopping and trapping behavior that
+  	characterizes solute center-of-mass trajectories in our MD simulations.
+  	\item The AD model did not suffer this qualitative shortcoming, but the 
+  	persistent curvature of the predicted MSD curves suggested that the model
+  	might underestimate MSDs on long timescales. 
+  	\item The formulation of both models required careful examination and
+  	characterization of the interactions and dynamics exhibit by MD trajectories 
+  	which required considerable human effort.
   \end{itemize}
@@
   % The former is definitely simpler.
-  In this work, we apply the infinite hidden markov model (iHMM), a modeling
+  % MRS: True.  I would probably see which is used more in the literature. 
+  % BJC1: going with IHMM. HDPHMM seems to mostly be used by Emily Fox
+  In this work, we apply the infinite hidden markov model (IHMM), a modeling
   approach that is agnostic to the source of time series data, in order to 
   automatically detect and infer the parameters of an unknown number of latent
-  autoregressive modes. \\
+  autoregressive (AR) modes present in solute center-of-mass time series.
+  \begin{itemize}
+  	\item In addition to AR parameters for each state, the IHMM estimates the
+  	state transition probability matrix.
+  	\item The model helps simultaneously uncover underlying transport mechanisms which
+  	give rise to dynamical behavior and project that behavior on longer timescales so
+  	that we can estimate macroscopic transport observables.
+  \end{itemize}
 
-  We study the same four solutes from our previous work. \\
+  We use the parameters of the states identified by the IHMM in order to infer 
+  dominant solute-membrane interactions and transport mechanisms.
+  \begin{itemize}
+    \item We compare the inferred mechanisms to those which we manually
+    identified in our previous work. 
+    \item Some kind of conclusion here. Did we find more or less states. Any new states/ subdivisions of states?
+  \end{itemize}
 
-  We use the iHMM to generate stochastic trajectory realizations that share the same
-  dynamical characteristics as solute trajectories observed in our MD simulations. 
+  We can also use the IHMM to generate stochastic trajectory realizations that share
+  the same dynamical characteristics as solute trajectories observed in our MD 
+  simulations. 
   \begin{itemize}
     \item The trajectories are qualitatively similar, showing expected hopping and trapping
-    behavior
-    \item They are quantitatively similar in that they reproduce the MSDs measured in MD
+    behavior.
+    \item They are quantitatively similar in that they reproduce the MSDs measured in MD.
   \end{itemize}
 
-  Finally, we use the stochastic trajectory realizations in order to compute the MFPT 
-  of solutes in macroscopic length pores.
+  Finally, we use the stochastic trajectory realizations in order to compute the 
+  macroscopic flux of each solute and selectivity of the LLC membranes studied towards
+  each solute.
   \begin{itemize}
-  	\item We relate the MFPT to flux and compare the fluxes between solutes to get selectivity.
+    \item We relate these macroscopic properties to our nanoscopic model by simulating 
+    mean first passage time (MFPT).
+    \item Some kind of conclusion. This membrane is selective towards solutes with this
+    functionality. 
+    \item Does the conclusion agree with our previous work? Any length dependence? (I think not)
   \end{itemize}
@@
 
-  \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}
+  \subsection{The Infinite State Hidden Markov Model}\label{method:IHMM}
   %BJC: There is a fair amount of detail here just so I could understand better by writing it out
@@
   %Based on the algorithms developed by Fox et al.~\cite{fox_sticky_2007}, 
-  Using the iHMM framework, we estimated the most likely number and sequence of hidden states
+  Using the IHMM framework, we estimated the most likely number and sequence of hidden states
   while simultaneously estimating VAR(1) parameters for each state and the overall 
@@
 
-  We generated stochastic realizations by drawing state sequences based on the
-  rows of $T$. 
-  %BJC: lots more implementation details once that is ironed out
+  We applied the IHMM algorithm to the radial and axial coordinates of each 
+  solute center-of-mass trajectory.
+  \begin{itemize}
+    \item We measured the radial coordinate as the distance from the closest
+    pore center.
+    \item Because the pores are somewhat tortuous, we approximated the pore 
+    center as a spline. See previous work.
+  \end{itemize}
+
+  We clustered like parameter sets in order to reduce the state space to
+  a more easily interpretable size.
+  \begin{itemize}
+    \item Since the mean vector, $\mathbf{c}$ of each state can take on 
+    continuous values, the IHMM algorithm tends to find a large number of states,
+    with very few states revisited.
+    % BJC1: This will need to be updated depending on how I cluster. Might need to describe
+    % multiple clustering approaches.
+    \item However, $\mathbf{A_i}$ and $\mathbf{\Sigma}$ tend to share similarities with
+    independently identified states. Therefore, we clustered based on $\mathbf{A_i}$
+    and $\mathbf{\Sigma}$, ignoring the mean.
+    \item Since  we do not know the number of similar states beforehand, we used
+    a non-parametric Bayesian Gaussian mixture model % cite scikit-learn
+    \item We used the clustered parameters in order to relabel states in the estimated
+    state sequences and to recalculate the state transition probability matrix.
+  \end{itemize}
+
+  We generated stochastic trajectory realizations by drawing state sequences 
+  based on the rows of $T$.
+  \begin{itemize}
+    \item While in a given state, we simulated motion according to the VAR(1)
+    parameterization of that state.
+    \item We set the unconditional mean of each state based on the position 
+    before the state transition occurred.
+  \end{itemize}
 
@@
 
+  \subsection{Inferring Solute Transport Mechanisms}
+
+  Clustering parameters sets results in X distinct dynamical modes.
+  \begin{itemize}
+    \item In the figure below, we show time series simulations that qualitatively
+    illustrate the difference in dynamical behavior between modes.
+  \end{itemize}
+
+  %BJC1: a figure showing some representative fluctuations in each mode
+
+  \noindent We can relate the identified states back to transport mechanisms.
+  \begin{itemize}
+  	\item More detailed discussion of identified states
+  	\item How size of fluctuations, autoregressive parameters are influenced by trapping mechanisms
+  	\item How do these states compare to those identified in our previous work?
+  	\item Any new states?
+  \end{itemize}
+
+  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}
+
   \noindent Trajectory realizations qualitatively match MD simulation trajectories.
@@
 
-  \noindent We can relate the identified states back to transport mechanisms.
-  \begin{itemize}
-  	\item More detailed discussion of identified states
-  	\item How size of fluctuations, autoregressive parameters are influenced by trapping mechanisms
-  	\item Any new states?
-  \end{itemize}
+  \subsection{Estimating Solute Flux and Selectivity}
 
@@
 
-  \noindent We have shown that the iHMM can be used to parameterize solute time series
+  \noindent We have shown that the IHMM can be used to parameterize solute time series
   with an unknown number of latent dynamical modes. \\
 
-  \noindent We can use the iHMM to help identify mechanisms by relating the latent
+  \noindent We can use the IHMM to help identify mechanisms by relating the latent
   states to observed solute behavior. \\
 
-  \noindent We can use the iHMM to predict macroscopic transport properties. \\
+  \noindent We can use the IHMM to predict macroscopic transport properties. \\
 
-  \noindent The iHMM is not limited to the H\textsubscript{II} phase.
+  \noindent The IHMM is not limited to the H\textsubscript{II} phase.
 
@@
 
-  \newpage
+  %\newpage
 
-  \section*{TOC Graphic}
+  %\section*{TOC Graphic}
 

### 2020-02-27 Ben_Manuscripts/thesis/intro.tex
Beefing up intro

@@
   \begin{itemize}
-    \item They can be classified based on the size of the particle they reject.
-    \item Microfiltration membranes contain 100-10000 nm pores. They can separate large
-    particles like bacteria and protozoa.~\cite{ma_functionalized_2014}
-    \item Ultrafiltration membranes have pore sizes about 5-500 nm and are useful for the 
-    separation of sugars, proteins, viruses and colloidal materials.~\cite{davey_ultrafiltration_2009}
-    \item Nanofiltration have pores on the order of 1 nm in size and can be used for the separation
+    \item Membranes are classified based on the size of the particle they reject.
+    \item Microfiltration membranes contain pores with diameters ranging from 100-10000 nm.
+    They can separate large particles like bacteria and protozoa.~\cite{ma_functionalized_2014}
+    \item Ultrafiltration membranes have pore diameters of about 5-500 nm and are useful for the 
+    separation of sugars, proteins, viruses and colloidal materials.~\cite{yanful_ultrafiltration_2009}
+    \item Nanofiltration have pores on the order of 1 nm in diameter and can be used for the separation
     of small organic molecules and charged species.~\cite{van_der_bruggen_review_2003}
     \item Reverse osmosis membranes are dense amorphous polymers with no explicit pores. Their
-    dense polymer architecture reject all solutes except water making them useful for 
-    separating hydrated ions from water.~\cite{warsinger_review_2018}
+    dense polymer architecture rejects all solutes to a high degree except for water making
+    them useful for separating hydrated ions from water.~\cite{warsinger_review_2018}
     \item We have summarized the uses of different classes of membrane 
@@
 
-  \noindent In amorphous membranes, water flux is modeled using the solution-diffusion 
+  In amorphous membranes, water and solute flux are modeled using the solution-diffusion 
   model.
@@
     gradient and then desorb into the permeate.
-    \item The solubility and diffusivity can be described in terms of the 
-    diffusive water and solute permeabilities ($P_w$ and $P_s$) respectively
+    \item The product of a component's solubility and diffusivity is commonly
+    referred to as its permeability, $P$.~\cite{wijmans_solution-diffusion_1995}
+    \item $P$ is an intrinsic material property and is thus independent of membrane
+    thickness.  % BJC: is intensive a more appropriate word than intrinsic?
+    \item The water permeability coefficient \textit{is} dependent on thickness, $\delta_m$,
+    and can be formulated in terms of the pure water permeability, $P_w$.
     \item \begin{equation}
@@
     \end{equation}
-    where B is a solute permeability coefficient and \Delta c_m is the concentration
+    where B is a solute permeability coefficient and $\Delta c_m$ is the concentration
     difference across the selective membrane layer.
@@
     \item Additionally, many membranes are not suited for high purity separations
-    of small neutral species which requires chemical and capital costs for
+    of small neutral species which necessitates chemical and capital costs for
     post-treatment
@@
 
-  Selective separations are useful for a wide range of applications.
+  Selective separations are useful in a wide range of applications.
 
-  % Put this with the desalination section below maybe
-  % morton_environmental_1996,bhojwani_technology_2019
   \textit{Desalination}:
@@
   	shown to be more environmently friendly and economical due to its lower energy
-  	requirements.
+  	requirements.\cite{morton_environmental_1996}
   	\item Thermal techniques are still preferred where excess waste heat or cheap 
-  	thermal energy is available, such as cogeneration plants.
-  	\item RO has smaller footprint?
+  	thermal energy is available, such as cogeneration plants.\cite{bhojwani_technology_2019}
+  	\item RO has smaller footprint % BJC: need citation
   \end{itemize}
@@
   \begin{itemize}
-    \item Micropollutants include pharmaceutical and personal care products, 
+    \item Micropollutants include pharmaceuticals, personal care products, 
     hormones, pesticides and industrial chemicals which find their way into
@@
   \textit{Recovery of Valuable Dissolved Species}: We can use highly selective
-  membranes in order to recover potentially valueable dissolved species from 
+  membranes in order to recover potentially valuable dissolved species from 
   complex waste streams.
@@
   \begin{itemize}  
-    \item Mostly desalination (?)
+    \item Desalination, concentration
     \item Typically you have a porous support layer for mechanical strength and 
@@
 
-  Operation requires high feed pressures.
+  Operation requires high feed pressures. (5 - 120 bar) ~\cite{van_der_bruggen_review_2003}
 
-  \subsection{Standard Nanofiltration}
+  \subsection{Standard Nanofiltration Membranes}
 
@@
 
-  Explicitly defined pores allows much lower feed pressures. However, polydispersity in
-  pore size lowers their selectivity relative to RO.
+  Explicitly defined pores allow lower feed pressures (3 - 20 bar),~\cite{van_der_bruggen_review_2003}
+  however, polydispersity in pore size lowers their selectivity relative to RO.
 
@@
 
-  %BJC: format for following paragraphs maybe: Introduce tech, say how it would work, why it doesn't work 
+  %BJC: More detail on these sections to come.
+  % Probable format for following paragraphs: Introduce tech, say how it would work, then why it doesn't work 
   Ultrathin-film
@@
     and have the potential to interact with solutes in a chemically-dependent manner.
-    \item In theory, this topology is ideal for high flux and highly selective separations.
+    \item In theory, this pore topology and geometry is ideal for high flux and 
+    highly selective separations.
   \end{itemize}
@@
   Unfortunately, it is a difficult task to align the self-assembled hexagonal
-  mesophases into continuous pores that traverse the width of the membrane.
+  mesophases into continuous pores that traverse the thickness of the membrane.
   \begin{itemize}
@@
     \item Feng et al. leverage the magnetic anisotropy of the columnar \
-    mesophases in order to control their alignment with a magnetic field~\cite{feng_scalable_2014}
-    \item Feng et al. also used an approach caused soft confinement which
+    mesophases in order to control their alignment with a magnetic field.~\cite{feng_scalable_2014}
+    \item Feng et al. also used an approach called soft confinement which
     takes advantage of the hexagonal columns preference towards anchoring
@@
   The space group of the Q\textsubscript{I} phase configuration formed by
-  monomer 1 is uncertain and thought to be either Pn3m or Ia3d.
+  monomer 1 is uncertain and thought to be either Pn3m or Ia3d.  %BJC: will have accompanying figure
   \begin{itemize}
@@
     dependent on system geometry.~\cite{mantha_dynamics_2016,roy_water_2016}
-    \item Jackson et al. as well as Manthan et al. have combined experiment with simulation
+    \item Jackson et al. as well as Mantha et al. have combined experiment with simulation
     in order to show how the choice of monomer head group counterion regulate water 

### 2020-03-08 Ben_Manuscripts/thesis/intro.tex
Some comments on intro.

@@
     are all common components of aqueous streams.
+%MRS: maybe talk about molecular separations are particularly hard (to set up the work you do).
   \end{itemize}
@@
     of small organic molecules and charged species.~\cite{van_der_bruggen_review_2003}
+    %MRS: no explicit pores might not quite be right. . . because there are pores there, just not designed pores. tortuous Pores formed by collapsed polymer networks? 
     \item Reverse osmosis membranes are dense amorphous polymers with no explicit pores. Their
@@
 
+%MRS: provide more of a context for this discussion.  Why are your reviewing this theory here?  
+%MRS: are you assuming solution/diffusion here? If so, state explicitly. 
+%MRS: OK after reading through, I have a suggestion.
+Maybe the theory section should to nearer to the end.
+At the beginning you talk more about membrane structure and applications, and talk about more traditional membranes, and then pivot to new membranes.
+Maybe you should stick with structure/function until you talk about the solute motion, and how it's NOT simple diffusioin, then talk about standard theory, then talk about the the need for alternative theory, and then introduce the ideas you will describe in much more detail in the chapters corresponding to your later papers.
+Does that make sense as a strategy?
   \noindent Membrane permeation is the result of a chemical potential gradient, $\frac{d\mu_i}{dx}$.
@@
 	  where $L_i$ is a coefficient of proportionality.~\cite{wijmans_solution-diffusion_1995}
+          %MRS2: mention what L depends on molecularly (even if uncalculatable)
 	  \item Chemical potential gradients can be induced by concentration, pressure, 
 	  temperature and electromotive forces.
-	  \item We will limit our discussion to concentration and pressure gradients.
+	  \item We will limit our discussion to concentration and pressure gradients. %MRS: mention why?
   \end{itemize}
 
+  %MRS: is there are reason you are talkling about just water flux here?
   % This follows the discussion of werber_material_2016
@@
 
+  %MRS: be clearer on presenting the context for this theory.  Will your findings be in contradiction?
+  %MRS: is this theory inadequate?  Will it be tested?
   In porous membrane architectures, water flux is modeled as laminar flow through 
@@
   membrane separations.
+  %MRS: citation?
   \begin{itemize}
@@
     more gains.
+    %MRS: math (or citations) for this statement?
  \end{itemize}
@@
 
+%MRS: Maybe the applications be presented before theory?
   Selective separations are useful in a wide range of applications.
@@
     \item Typically you have a porous support layer for mechanical strength and 
-    very thin active layer where the separations occur.
+    very thin active layer where the 
+%MRS: added
+molecular/nanoscale
+separations occur.
     \item Usually only let water through. Usually have to remineralize the
@@
   \subsection{Standard Nanofiltration Membranes}
-
+  %MRS: is explicitly defined the right word?  ``Created pores?''
   Unlike RO membranes, NF membranes have explicitly defined pores. An
@@
 	\item Practically, dispersing and aligning CNTs into a polymer matrix is extremely
-    difficult because they tend to agglomerate due to Van der Waals forces.~\cite{sahoo_polymer_2010}
+    difficult because they tend to agglomerate due to van der Waals forces.~\cite{sahoo_polymer_2010}
     \item Some work has been to functionalize the carbon nanotubes in order to better incorporate them. % need reference
@@
 
+%MRS: probably could generalize to self-assmbled porous materials as
+%the class in general, and the cross-linked LLC's as a particular exemplar.
+
   \section{Cross-linked Self Assembled Liquid Crystal Membranes for Selective Aqueous Separations}
@@
 
+  %MRS: be more explicit what you mean by ``study''.
   In this work we study LLC membranes as an alternative nanostructured material for 
@@
     and have the potential to interact with solutes in a chemically-dependent manner.
+    %MRS: could discuss concept that the effective pore size depends on the solute.
     \item In theory, this pore topology and geometry is ideal for high flux and 
@@
 
+  %MRS: be more explicit that this is synthesis of usable amounts of
+  %actual separations membranes, not the molecules themselves.
   Due to its more facile synthesis, there has been significantly more development
@@
   less than 1.2 nm in diameter because the pores are too large
+  %MRS: this above is interesting, since that seems somewhat inconsistent with the 
   \cite{zhou_supported_2005}. We do not yet understand how to controllably reduce
@@
     	\end{itemize}
+    %MRS: maybe talk more about the stochastic modeling itself; for example, could phrase it in terms of
+    %how you can test mechanistic models to see if they are consistent with the timeseries, and then how those models
+    %can be further extrapolated to physical observables even if the MD simulations cannot. 
+    %MRS: this MIGHT include using the effective diffusion in a solution/diffusion model.
     \item Can we estimate experimentally-relevant macroscopic properties?
@@
     	\end{itemize}
+    %MRS: this might be overly ambitions.  Maybe something more like: How can the timeseries data inform us about the mechanism directly?
     \item How can we learn mechanisms with minimal human intervention?  %BJC: i.e. machine learning methods

### 2020-03-09 Ben_Manuscripts/hdphmm/Outline.tex
Comments.

@@
   separations of components of complex aqueous streams.
+  %MRS2: add some more examples (When you get around to it).
   \begin{itemize}
@@
   	\item In both cases the pores are uniform in size with radii on the order of 1 nm
+         %MRS2: is it really a molecular weight cutoff?
   	giving them a very strict molecular weight cut-off.
@@
     about the molecular origins of separation processes.
+    %MRS2: not quite sure what you mean below?
     \item This drives an empirical design approach which can potentially neglect key
@@
   \begin{itemize}
+    %MRS2: would be good to get this next point into the first line of a paragraph, since it's quite important. 
     \item However, if we use descriptive stochastic models that can capture solute
@@
   % BJC1: going with IHMM. HDPHMM seems to mostly be used by Emily Fox
-  In this work, we apply the infinite hidden markov model (IHMM), a modeling
+  In this work, we apply the infinite hidden Markov Model (IHMM), a modeling
   approach that is agnostic to the source of time series data, in order to 
@@
     identified in our previous work. 
+    %MRS2: don't put the conclusions in the introduction.  Instead, state clearly the questions you will ask and the hypotheses you will test.
    \item Some kind of conclusion here. Did we find more or less states. Any new states/ subdivisions of states?
@@
   \begin{itemize}
+    %MRS2: shouldn't reach conclusions in intro, just set up questions to be answered (conclusions SHOULD be in abstract).
     \item We relate these macroscopic properties to our nanoscopic model by simulating 
@@
     \item Appropriate stochastic modeling requires that solutes sample the 
-    accessible mechanisms with representative probability.
+    accessible mechanisms with representative probability.%MRS: only possible on the ~1-10 \mu scale with relatively fast solutes.
   \end{itemize}
@@
   in a sequence depends only on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
+  %MRS2: it can depend on other things, but ALSO depends on the latent state.
   \begin{itemize}
@@
   	vector $\mathbf{c}$ and a white noise term $\mathbf{e}_t$.~\cite{hamilton_time_1994}
+        %MRS2: mean is zero in Z, is it necessarily in R (I realize we've talked about this before, but wanted to get the clarification in text)
   	\item We assumed multivariate Gaussian noise, with mean zero and covariance, $\Sigma$.
@@
     center as a spline. See previous work.
+    %MRS2: approximated the pore center line with a spline?
   \end{itemize}
@@
   \begin{itemize}
+    %MRS2: can you enforce that the mean in the z-component is zero?
+    %MRS2: I'm trying to think what other constraints should be enforced. 
+    %MRS2: the issue with state clustering is that when transitionin between two states that are clustered, 
+    %MRS2: it destroys the correlation that would have been within if it was all the same statee.
+    %MRS2: I'm not sure what the implications are. If the simulations are RUN with grouped states, 
+    %MRS2: then the correlation can be reintroduced, so maybe it doesn't matter?
    \item Since the mean vector, $\mathbf{c}$ of each state can take on 
@@
   \section{Results and Discussion}
-
+  %MRS2: how stable are the results to realizations of the system
   \subsection{Inferring Solute Transport Mechanisms}
@@
   \noindent Trajectory realizations qualitatively match MD simulation trajectories.
+
   \begin{itemize}
+    %MRS2: think about how to quantify the simiilarity of the hopping and trapping behavior.
     \item Look for hopping and trapping behavior
@@
   \begin{itemize}
+    %MRS2: again, think about the best ways to quantify similar between MD and stochastic trajectories.
   	\item Look at curvature and 1-$\sigma$ confidence intervals
@@
 
+  %MRS2: below probably doesn't need to be stated?
   \noindent The IHMM is not limited to the H\textsubscript{II} phase.
@@
 
+  %MRS2: add GAANN and PRF here to cover bases.
   Molecular simulations were performed using the Extreme Science and

### 2020-03-10 Ben_Manuscripts/hdphmm/Outline.tex
Adding citations and beef to intro

@@
     %MRS2: is it really a molecular weight cutoff?
-  	giving them a very strict molecular weight cut-off.
+    %BJC2: is molecular size better? Obviously there are other factors like shape, but I don't want to get into that
+  	giving them a very strict molecular size cut-off.
 	\item Additionally, they have the potential to disrupt conventional membrane separation
@@
   for modeling sequences of observations where the probability of the next observation
-  in a sequence depends only on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
+  in a sequence depends on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
   %MRS2: it can depend on other things, but ALSO depends on the latent state.
@@
     \item Because the pores are somewhat tortuous, we approximated the pore 
-    center as a spline. See previous work.
+    center with a spline. See previous work.
     %MRS2: approximated the pore center line with a spline?
@@
   %MRS2: add GAANN and PRF here to cover bases.
+  This work was supported in part by the ACS Petroleum Research Fund
+  grant \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN) 
+  fellowship which is funded by the U.S. Department of Education. 
   Molecular simulations were performed using the Extreme Science and

### 2020-03-10 Ben_Manuscripts/thesis/intro.tex
Adding citations and beef to intro

--- 2020-02-27 Ben_Manuscripts/thesis/intro.tex
@@
     are all common components of aqueous streams.
+    \item The diversity in size and chemical topology of contaminants makes the
+    design of membrane processes meant to separate these components complex.
+    \item To deal with complex aqueous streams, and to prevent excessive membrane
+    fouling, multiple types of membranes are often used in series, removing 
+    larger particles first.~\cite{goosen_fouling_2005}
   \end{itemize}
@@
   % TFC membranes review -- "Composite reverse osmosis and nanofiltration membranes"
-  \noindent Membrane design is completely dependent on the target particle separation. 
+  \noindent Modern membrane design is completely dependent on the target particle 
+  separation. 
   \begin{itemize}
-    \item Membranes are classified based on the size of the particle they reject.
-    \item Microfiltration membranes contain pores with diameters ranging from 100-10000 nm.
-    They can separate large particles like bacteria and protozoa.~\cite{ma_functionalized_2014}
-    \item Ultrafiltration membranes have pore diameters of about 5-500 nm and are useful for the 
+    \item Separation membranes are most broadly classified based on the size of 
+    the particle they reject.
+    \item Microfiltration (MF) membranes contain pores with diameters ranging from 
+    100-10000 nm. They can separate large particles like bacteria and protozoa.~\cite{ma_functionalized_2014}
+    \item Ultrafiltration (UF) membranes have pore diameters of about 5-500 nm and are useful for the 
     separation of sugars, proteins, viruses and colloidal materials.~\cite{yanful_ultrafiltration_2009}
-    \item Nanofiltration have pores on the order of 1 nm in diameter and can be used for the separation
-    of small organic molecules and charged species.~\cite{van_der_bruggen_review_2003}
-    \item Reverse osmosis membranes are dense amorphous polymers with no explicit pores. Their
-    dense polymer architecture rejects all solutes to a high degree except for water making
-    them useful for separating hydrated ions from water.~\cite{warsinger_review_2018}
-    \item We have summarized the uses of different classes of membrane 
-    technologies in Figure~\ref{fig:size_regimes}.
-    \item To deal with complex aqueous streams, and to prevent excessive membrane fouling, 
-    these technologies are often used in series, removing larger particles first.~\cite{goosen_fouling_2005}
+    \item Nanofiltration (NF) membranes have pores on the order of 1 nm in diameter and can 
+    be used for the separation of small organic molecules and charged species.~\cite{van_der_bruggen_review_2003}
+    \item Reverse osmosis (RO) membranes are dense amorphous polymers with tortuous 
+    pathways formed by collapsed polymer networks. Their dense polymer architecture 
+    rejects all solutes to a high degree except for water making them useful for 
+    separating hydrated ions from water.~\cite{warsinger_review_2018}
+    \item We have summarized the uses of the different classes of membrane technologies in 
+    Figure~\ref{fig:size_regimes}.
   \end{itemize}
@@
   \includegraphics[width=\textwidth]{figs/membrane_separation_size_regimes.pdf}
-  \caption{}\label{fig:size_regimes}
+  \caption{Caption of the future}\label{fig:size_regimes}
   \end{figure}
 
-  \noindent Membrane permeation is the result of a chemical potential gradient, $\frac{d\mu_i}{dx}$.
+  Membranes are generally designed to maximize two key performance metrics: 
+  permeability and selectivity.
   \begin{itemize}
-	  \item The flux of component $i$ is proportional to this gradient:
-	  \begin{equation}
-	    J_i = -L_i \frac{d\mu_i}{dx}
-	  \end{equation}
-	  where $L_i$ is a coefficient of proportionality.~\cite{wijmans_solution-diffusion_1995}
-	  \item Chemical potential gradients can be induced by concentration, pressure, 
-	  temperature and electromotive forces.
-	  \item We will limit our discussion to concentration and pressure gradients.
-  \end{itemize}
-
-  % This follows the discussion of werber_material_2016
-  For pressure driven membrane processes, water flux through both porous and 
-  amorphous membranes can be described by
-  \begin{equation}
-  J_w = A(\Delta P - \Delta \pi_m)
-  \end{equation}
-  where $J_w$ is volumetric water flux, $A$ is the water permeability coefficient,
-  $\Delta P$ is the applied hydraulic pressure and $\Delta \pi_m$ is the 
-  trans-membrane osmotic pressure difference. The water permeability coefficient
-  is dependent on how one models flow through the membrane.
-
-  In porous membrane architectures, water flux is modeled as laminar flow through 
-  cylindrical pores.
-  \begin{itemize}
-    \item The derivation follows Hagen-Poiseuille flow with inclusion of morphological
-    characteristics:
-    \begin{equation}
-      A = \frac{\varepsilon r_p^2}{8\mu\delta_m}
-    \end{equation}
-    where $\varepsilon$ is the surface porosity, $r_p$ the pore radius, $\delta_m$ the
-    membrane thickness, and $\mu$ the solution viscosity.
-    \item Separation is typically characterized in terms of solute rejection, $R$. 
-    \begin{equation}
-      R = 1 - \frac{c_p}{c_f}
-    \end{equation}
-    where $c_p$ and $c_f$ are the concentrations of the rejected species in
-    the permeate and feed respectively.
-    \item Solutes with radii smaller than the pore will be rejected. A distribution of 
-    pore sizes prevents perfect rejection.
-  \end{itemize}
-
-  In amorphous membranes, water and solute flux are modeled using the solution-diffusion 
-  model.
-  \begin{itemize}
-    \item It is hypothesized that water and solute molecules partition into the
-    membrane and diffuse across the polymer matrix due to a chemical potential
-    gradient and then desorb into the permeate.
-    \item The product of a component's solubility and diffusivity is commonly
-    referred to as its permeability, $P$.~\cite{wijmans_solution-diffusion_1995}
-    \item $P$ is an intrinsic material property and is thus independent of membrane
-    thickness.  % BJC: is intensive a more appropriate word than intrinsic?
-    \item The water permeability coefficient \textit{is} dependent on thickness, $\delta_m$,
-    and can be formulated in terms of the pure water permeability, $P_w$.
-    \item \begin{equation}
-    A = \frac{P_wV_w}{\delta_mR_gT}
-    \end{equation}
-    where $V_w$ is molar volume of water, $R_g$ is the gas constant and $T$ is
-    absolute temperature.
-    \item Solute flux is modeled as:
-    \begin{equation}
-    J_s = \frac{P_s}{\delta_m}\Delta c_m = B\Delta c_m
-    \end{equation}
-    where B is a solute permeability coefficient and $\Delta c_m$ is the concentration
-    difference across the selective membrane layer.
-    \item Under these assumptions, rejection can be reformulated as
-    \begin{equation}
-    R = \frac{A}{A + B}
-    \end{equation}
-    which approaches unity as the solute flux tends towards zero.
+    \item Permeability is used to quantify the rate at which solvent and solutes
+    pass through the membrane.
+    \item Selectivity quantifies the relative rates of passage of two substances.
+    \item A related quantity to selectivity, rejection, quantifies the fraction
+    of undesired solute that does not pass through the membrane.
   \end{itemize}
@@
   selectivity may offer a more effective route towards lowering the cost of 
-  membrane separations.
+  membrane separations.~\cite{werber_materials_2016}
   \begin{itemize}
@@
     \item Cohen-Tanugi et al. calculated that tripling membrane permeability
-    could reduce energy consumption up to 15\% in a seawater reverse osmosis plant.~\cite{cohen-tanugi_quantifying_2014}
+    could reduce energy consumption up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
     \item Perhaps the biggest detriment to energy consumption is the practical
@@
     of small neutral species which necessitates chemical and capital costs for
-    post-treatment
+    post-treatment.
     \item Addressing these problems with highly selective separations may lead to 
     more gains.
+    %MRS: math (or citations) for this statement?
  \end{itemize}
 
-%  These equations provide a somewhat limited perspective on the molecular details
-%  of transport.
-%  \begin{itemize}
-%    \item The parameters are experimental observables which allow one to 
-%    speculate on the atomic-level 
-%  \end{itemize}
+  \subsection{Applications of Selective Membranes}
 
-  \subsection{Applications of Selective Membranes}
+  %BJC2: this section needs meat and citations
 
@@
   \begin{itemize}
-  	\item Compared with thermal distillation techniques, reverse osmosis has been 
-  	shown to be more environmently friendly and economical due to its lower energy
-  	requirements.\cite{morton_environmental_1996}
+  	\item Compared with thermal distillation techniques, RO has been shown to 
+  	be more environmently friendly and economical due to its lower energy
+  	requirements.\cite{morton_environmental_1997}
+ 	\item In general, RO has a smaller footprint % BJC: need citation
   	\item Thermal techniques are still preferred where excess waste heat or cheap 
   	thermal energy is available, such as cogeneration plants.\cite{bhojwani_technology_2019}
-  	\item RO has smaller footprint % BJC: need citation
   \end{itemize}
@@
   Municipal and industrial wastewaters are contaminated by harmful
-  micropollutants, which have adverse effects on human health even at low 
-  concentrations\cite{schwarzenbach_challenge_2006}
+  micropollutants, which can have adverse effects on human health even at low 
+  concentrations.\cite{schwarzenbach_challenge_2006}
   \begin{itemize}
@@
     hormones, pesticides and industrial chemicals which find their way into
-    our drinking water supply
+    our drinking water supply.
+    %BJC2: There is a review I need to wade through to bulk this up.
     \item Is there any infrastructure built to combat this?
@@
   Municipal waste-waters are rich in carbon, nitrogen and phosphorus-containing 
-  compounds. 
+  compounds. % i.e. poop
   \begin{itemize}  
@@
     prompted the use of separation technologies such as RO and NF in order to 
-    reduce the volume of contaminated water~\cite{gregory_water_2011}.
+    reduce the volume of contaminated water.~\cite{gregory_water_2011}
     \item Some of the dissolved organic compounds in flowback water, such as acetate, 
@@
   \textit{Breathable barriers}:
+
   Finally, there is a great deal of military interest in creating breathable 
@@
   \section{Competing Membrane Technologies}
+  %BJC2: maybe better to title this section "Historical Development of Membrane Technology"
 
-  \subsection{Amorphous Membranes}
+  Membranes for separations are a relatively young technology. Over the past 60 years, 
+  the field has grown into a commercially viable technology and the focus has shifted
+  primarily towards incremental improvements in performance and most importantly,
+  targeted separations. This section will briefly cover a subset of the most relevant
+  membrane technologies which have ultimately inspired this thesis.
 
-  Amorphous thin film composite (TFC) RO membranes are the current industry standard for
-  high purity separations.
+  \subsection{Reverse Osmosis Membranes}
+
+  The first aqueous separations membranes were developed for RO applications 
+  in the 1960s and were made of the amorphous polymer cellulose acetate (CA).~\cite{kesting_semipermeable_1965}
   \begin{itemize}
-    \item Desalination, concentration
-    \item Typically you have a porous support layer for mechanical strength and 
-    very thin active layer where the separations occur.
-    \item Usually only let water through. Usually have to remineralize the
-    water to make it drinkable.
+    \item Reid and Spencer were among the first to show the ability of
+    these membranes to reject NaCl to high degrees ($\sim$ 99 \%) while subject 
+    to high applied pressures (270 atm).~\cite{reid_ultrafiltration_1960}
+    \item The most limiting drawback to CA membranes is their chemical instability, 
+    undergoing severe hydrolysis at pH values outside the range 4--6.~\cite{vos_kinetic_1966}
   \end{itemize}
 
-  Operation requires high feed pressures. (5 - 120 bar) ~\cite{van_der_bruggen_review_2003}
-
-  \subsection{Standard Nanofiltration Membranes}
-
-  Unlike RO membranes, NF membranes have explicitly defined pores. An
-  ideal NF membrane should have densely packed, uniform-sized and
-  non-tortuous pores. This combination has been very difficult to realize.
-
-  NF membranes are typically made by a phase-inversion process. The most 
-  widely used phase-inversion process is immersion precipitation.
+  Amorphous thin film composite (TFC) polyamide membranes are the current industry 
+  standard for high purity RO separations.~\cite{baker_membrane_2012}
   \begin{itemize}  
-    \item During which one submerges a polymer, dissolved in a solvent, in
-    a non-solvent.
-    \item A solid, porous polymer membrane is all that remains once all
-    solvent has been removed by non-solvent exchange \cite{smolders_microstructures_1992}.
-    \item The resultant pores are polydisperse in size, which hurts membrane selectivity. 
+    \item Developed in the 1980s, polyamide membranes are capable of rejecting salt
+    to a higher degree and can operate at wider pH ranges and higher feed pressures than 
+    CA membranes.~\cite{cadotte_interfacial_1981}
+    \item TFC polyamide membranes are typically formed by the interfacial polymerization
+    of a polyamide selective layer on the surface of a microporous polysulfone support 
+    layer.    
+    \item The support layer gives the membrane mechanical strength without hindering the
+    flow of water thereby permitting a very thin selective layer where molecular 
+    separations occur.~\cite{kucera_biofouling_2019}
   \end{itemize}
 
-  A second technique used to create NF membranes is call track-etching in which a polymer
-  film is bombarded with charged particles, then chemically etched to create pores
-  \cite{apel_track_2001}. The pores are uniform, which benefits selectivity;
-  however, the membranes have a low porosity and subsequently low permeability.
+  The dense polyamide selective layers of TFC membranes require high feed pressures,
+  in the range of 5 -- 120 bar, in order to achieve a useful permeate flux.~\cite{van_der_bruggen_review_2003}
+  \begin{itemize}
+    \item While the energy requirements to attain these pressures are still less than 
+    the energy requirements of thermal distillation\cite{morton_environmental_1997}, it 
+    is often desirable to create membranes that can operate at lower feed pressures.
+    %BJC2: probably could use some citations here
+    \item It is not always necessary to achieve the high purity permeate streams
+    resulting from RO.
+    \item It is also possible that a target separation may be possible with 
+    membranes containing larger pores.
+    \item This has driven research into nanofiltration.
+  \end{itemize}
 
-  Explicitly defined pores allow lower feed pressures (3 - 20 bar),~\cite{van_der_bruggen_review_2003}
-  however, polydispersity in pore size lowers their selectivity relative to RO.
+  \subsection{Nanofiltration Membranes}
+
+  Nanofiltration membranes have pores on the order of 1 nm in size. Larger pore sizes 
+  allow lower operating pressures (3 -- 20 bar) which lowers energy consumption.~\cite{van_der_bruggen_review_2003}
+  An ideal NF membrane should have densely packed, uniform-sized and non-tortuous pores.
+  This combination has been practically difficult to realize.
+
+  The most widely used methods of NF membrane fabrication are interfacial polymerization
+  and phase inversion.
+  \begin{itemize}
+    \item By modifying the monomer materials, one can control the structural morphology
+    produced by interfacial polymerization to create pores larger than those in RO
+    membranes.~\cite{seman_nanofiltration_2010}
+    \item During phase inversion, one submerges a polymer, dissolved in a solvent, in
+    a non-solvent. A solid, porous polymer membrane is all that remains once all
+    solvent has been removed by non-solvent exchange.~\cite{smolders_microstructures_1992}
+    \item Although commercially dominant, both of these techniques suffer from
+    tortuous pores and polydisperse pore sizes which results in far from ideal 
+    selectivities.
+  \end{itemize}
+
+  Track-etching is another technique which attempts to eliminate polydispersity and tortuosity.
+  During track-etching, a polymer film is bombarded with charged particles, then chemically 
+  etched to create pores.~\cite{apel_track_2001}
+  \begin{itemize}
+	\item Although the pores are uniform and non-tortuous, benefitting selectivity, the 
+	membranes have an extremely low pore density subsequently low permeability. 
+  \end{itemize}
+
+  %BJC2: maybe one more paragraph here with applications
 
@@
   interest typically have explicit nm-size pores that are uniform in size, eliminating
-  issues with polydispersity. There have been a number explorations into different
+  issues with polydispersity. There have been a number of explorations into different
   kinds of technologies for this application.
 
-  %BJC: More detail on these sections to come.
-  % Probable format for following paragraphs: Introduce tech, say how it would work, then why it doesn't work 
-  Ultrathin-film
-  graphene and graphene oxide membranes are an active area of research because
-  they are atomically thick and therefore offer potential for extremely high
+  %BJC2: would a figure showing the nanostructures go well here? (a graphene film, a carbon nanotube, a MOF, a zeolite)
+
+  %BJC2: Each tecnhology below will likely have its own heading and be split into 2 or more 
+  % paragraphs.
+
+  Ultrathin-film graphene and graphene oxide membranes are an active area of research because
+  they are atomically thick materials and therefore offer potential for extremely high
   permeability membranes.~\cite{humplik_nanostructured_2011} 
   \begin{itemize}
-    \item However, scalable synthesis without introducing microscopic, performance
-    degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
+    \item The tightly packed aromatic network of $sp^2$ hybridized carbon atoms that 
+    make up graphene sheets precludes the passage of even the smallest monoatomic species, helium.~\cite{bunch_impermeable_2008}
+    \item Controllably-sized pores have been created in pristine graphene by plasma etching
+    and by charged particle bombardment.~\cite{surwade_water_2015,russo_atom-by-atom_2012}
+    \item Graphene oxide (GO), a highly oxidized modification of graphene, consist of epoxy,
+    hydroxyl and carboxylate functional groups.~\cite{hegab_graphene_2015}
+    \item Many groups study GO membranes because they have improved antibacterial properties 
+    over graphene, leading to less membrane fouling, and because their functionality can be
+    modified in order to achieve solute-specific separations.~\cite{liu_antibacterial_2011,he_bioinspired_2013}
+    \item Despite their promise, scalable synthesis of monolayer graphene and GO membranes without
+    introducing microscopic, performance degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
+    \item Multilayered GO membranes have shown considerably more progress since their 
+    synthesis procedures are low cost and scalable.~\cite{zhang_size-controlled_2009}
+    \item GO sheets are particularly easy to make into multilayered membranes since they 
+    stack on top of each other, held together by hydrogen bonds.~\cite{homaeigohar_graphene_2017}
+    \item The potential of graphene and GO membrane certainly merits their continued exploration. Many
+    groups are still working in order to work on better control and standardization of their synthesis,
+    improving their designability for specific separations, and further improving their scalability.~\cite{wei_multilayered_2018}
   \end{itemize}
@@
   Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
-  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001}
+  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011}
   \begin{itemize}
+    \item CNTs are an allotrope of carbon consisting of tubular graphitic layers.~\cite{iijima_helical_1991}
+    \item One can control CNT diameters down to 0.5 nm in size which has inspired the
+    creation of CNT membranes for reverse osmosis applications.~\cite{sun_creating_2000}
+    \item Molecular dynamics simulations have predicted and experiments have confirmed that
+    CNTs are extremely fast transporters of water.~\cite{hummer_water_2001,joseph_why_2008}
+    \item MD simulations by Kalra et al. predicted water transport at rates comparable
+    to the transmembrane protein aquaporin-1.~\cite{kalra_osmotic_2003}
+    \item Experiments have exhibited water transport rates orders of magnitude higher than 
+    predictions by continuum modeling.~\cite{holt_fast_2006}
+    \item This enhancement has been explained as a result of nearly friction-less single-file water
+    flow through the hydrophobic CNT interiors.~\cite{kalra_osmotic_2003}
+    \item Functionalization of the CNT pore entrances can potentially lead to highly selective separations.~\cite{fornasiero_ion_2008}
 	\item Practically, dispersing and aligning CNTs into a polymer matrix is extremely
-    difficult because they tend to agglomerate due to Van der Waals forces.~\cite{sahoo_polymer_2010}
-    \item Some work has been to functionalize the carbon nanotubes in order to better incorporate them. % need reference
+    difficult because they tend to agglomerate due to van der Waals forces.~\cite{sahoo_polymer_2010}
+    \item Some work has been to functionalize the carbon nanotubes in order to better incorporate them,
+    however facile incorporation at scale remains a challenge yet to be overcome.~\cite{kim_polysulfone_2007}
   \end{itemize}
 
-  Zeolite-coated ceramic membranes offer the potential for permeabilities
-  comparable to ultrafiltration, with selectivities as good as NF and RO.%BJC: werber a possible reference?
+  Zeolite membranes offer the potential for permeabilities comparable to ultrafiltration, 
+  with selectivities as good as NF and RO.~\cite{hoek_nanotechnology-based_2014}
   \begin{itemize}  
+    \item Zeolites have highly uniform nm-sized crystalline structures with cage-like
+    cavities that allow movement and trapping of small solutes. 
+    \item The crystalline frameworks are typically formed by networks of silicon 
+    and aluminum each attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
+    \item One can replace the silicon and aluminum atoms via ion exchange in order
+    to control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}
+    \item Zeolite-coated ceramic membranes have shown the most promise for RO applications
+    because of their mechanical stability under high applied pressure and chemical
+    stability for withstanding disinfectants.~\cite{pendergast_review_2011}
     \item A number of studies have tested the permeability and sodium salt rejection
-    of various zeolite membranes, however none have fully overcome the
-    permeability-selectivity tradeoff.~\cite{pendergast_review_2011,auerbach_handbook_2003,li_novel_2007}
+    of various zeolite membranes, however their high permeabilities typcially come
+    at the cost of low selectivities and vice versa.~\cite{li_desalination_2004,duke_seawater_2009}
+    \item Zeolites are also prone to defects in the crystalline structure which 
+    would require substantial modification to the traditional synthesis procedures
+    in order to fix.~\cite{kumakiri_application_2000}
   \end{itemize}
@@
   \begin{itemize}
-    \item They were orginally used for gas separations
+    \item MOFs are highly porous and flexible crystalline structures made of metal
+    clusters coordinated to organic ligands.~\cite{furukawa_chemistry_2013}
+    \item There is a much wider breadth of research into MOFs as gas separation membranes
+    because they tend to be unstable in water.~\cite{feng_construction_2013}
+    \item But a new generation of water-stable MOFs is making it possible to use them
+    in aqueous separations.~\cite{wang_ultrastable_2015}
+    \item Purification of both aqueous and gaseous streams using MOFs are 
+    typically achieved by selective adsorption or catalytic degradation.~\cite{li_metalorganic_2012}    
+    \item MOFs have been applied towards the removal of a number of common water 
+    contaminants including dyes, pesticides, endocrine disruptors, and pharmaceuticals.
+    \cite{zhang_fabrication_2015,seo_adsorptive_2015,li_metalorganic_2015,hasan_adsorptive_2012}
+    \item Although aqueous MOF separations are theorized to surpass the performance 
+    of conventional membrane separations, it is still a budding field. The stability and
+    reusability of the material must be guaranteed before they can be implemented
+    at scale.~\cite{dias_towards_2015}
   \end{itemize}
@@
   \section{Cross-linked Self Assembled Liquid Crystal Membranes for Selective Aqueous Separations}
+
+  Amphiphilic molecules that self-assemble to form ordered nanostructures have shown
+  potential as nanoporous membranes.
+  \begin{itemize}
+    \item Block copolymers
+    \item Some other amphiphilic self-assembled thing
+    \item Liquid crystals as the guy we are studying because we have lots of 
+    experimental data.
+  \end{itemize}
 
@@
 
-  In this work we study LLC membranes as an alternative nanostructured material for 
-  highly selective aqueous separations.
+  In this work we attempt to understand how one can design LLC membranes as 
+  alternative nanostructured materials for highly selective aqueous separations.
 
@@
     and have the potential to interact with solutes in a chemically-dependent manner.
+    \item The inhomogeneity of the pores suggests that the effective pore size may depend
+    on the solute. Both the size, shape and chemical functionality will influence
+    how a solute partitions within the membrane. %BJC2: need to rework this sentence.
     \item In theory, this pore topology and geometry is ideal for high flux and 
@@
     molecule into ordered columnar phases.~\cite{feng_highly_2017}
+    \item Aligned hexagonal phase membranes exhibited an 85 fold increase in 
+    ionic conductivity.~\cite{feng_scalable_2014}
   \end{itemize}
@@
   The bicontinuous cubic, or Q\textsubscript{I} phase, is a class 
-  of nanostructured phases characterized by 3D interconnected pores.
+  of nanostructured phases characterized by a network of 3 dimensionally
+  interconnected pores.
   \begin{itemize}
@@
   Due to its more facile synthesis, there has been significantly more development
-  of Q\textsubscript{I} phase-forming monomers.
+  of Q\textsubscript{I} phase membranes.
   \begin{itemize}
@@
 
-  \section{Atomistic Molecular Simulation of LLC Membranes}
+  %\section{Atomistic Molecular Simulation of LLC Membranes}
+  \section{Modeling Membrane Separations}
+
+  %BJC2: taken from stochastic transport paper.
+  Mathematical descriptions of transport in complex separations membranes are a
+  powerful way to understand mechanisms and formulate design principles.
+  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
+  The complexity of a well-fit model generally parallels the complexity of the
+  transport mechanism being studied, as well as the transport information the
+  model conveys. In dense homogeneous membranes, the solution-diffusion model
+  can extract diffusion and partition coefficients and has successfully
+  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
+  Analogously, pore-flow models yield predictions of diffusion coefficients and
+  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
+  Modern single particle tracking approaches have taken researchers beyond
+  continuum modeling allowing them to characterize complex diffusive
+  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
+  molecular dynamics (MD) simulations to study both single particle dynamics
+  and bulk transport properties with atomic-level
+  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
+  approaches facilitate generation of hypotheses about the molecular origins of
+  separations by attempting to give a more intuitive understanding of how
+  solutes move as a function of their environment, in turn suggesting
+  experiments that could be performed.
+
+  \subsection{Macroscopic Treatments}
+
+  The most widely used approaches to modeling transport in membranes of all types
+  are based on macroscopic theory. In this section we will discuss the two prevailing
+  theories: the pore flow model and the solution-diffusion model.
+
+  %BJC2: add more citations
+  \noindent Membrane permeation is the result of a chemical potential gradient, $\frac{d\mu_i}{dx}$.
+  \begin{itemize}
+	  \item The flux of component $i$ is proportional to this gradient:
+	  \begin{equation}
+	    J_i = -L_i \frac{d\mu_i}{dx}
+	  \end{equation}
+	  where $L_i$ is a coefficient of proportionality.~\cite{wijmans_solution-diffusion_1995}
+      %MRS2: mention what L depends on molecularly (even if uncalculatable)
+	  \item Chemical potential gradients can be induced by concentration, pressure, 
+	  temperature and electromotive forces.
+	  \item We will limit our discussion to concentration and pressure gradients. %MRS: mention why?
+  \end{itemize}
+
+  %MRS: is there are reason you are talkling about just water flux here?
+  % This follows the discussion of werber_material_2016
+  %BJC2: add solute flux
+  For pressure driven membrane processes, water flux through both porous and 
+  amorphous membranes can be described by
+  \begin{equation}
+  J_w = A(\Delta P - \Delta \pi_m)
+  \end{equation}
+  where $J_w$ is volumetric water flux, $A$ is the water permeability coefficient,
+  $\Delta P$ is the applied hydraulic pressure and $\Delta \pi_m$ is the 
+  trans-membrane osmotic pressure difference. The water permeability coefficient
+  is dependent on how one models flow through the membrane.
+
+  %MRS: be clearer on presenting the context for this theory.  Will your findings be in contradiction?
+  %MRS: is this theory inadequate?  Will it be tested?
+  In porous membrane architectures, water flux is modeled as laminar flow through 
+  cylindrical pores.
+  \begin{itemize}
+    \item The derivation follows Hagen-Poiseuille flow with inclusion of morphological
+    characteristics:
+    \begin{equation}
+      A = \frac{\varepsilon r_p^2}{8\mu\delta_m}
+    \end{equation}
+    where $\varepsilon$ is the surface porosity, $r_p$ the pore radius, $\delta_m$ the
+    membrane thickness, and $\mu$ the solution viscosity.
+    \item Separation is typically characterized in terms of solute rejection, $R$. 
+    \begin{equation}
+      R = 1 - \frac{c_p}{c_f}
+    \end{equation}
+    where $c_p$ and $c_f$ are the concentrations of the rejected species in
+    the permeate and feed respectively.
+    \item Solutes with radii smaller than the pore will be rejected. A distribution of 
+    pore sizes prevents perfect rejection.
+  \end{itemize}
+
+  % BJC: mention does not enter Brownian regime
+  In amorphous membranes, water and solute flux are modeled using the solution-diffusion 
+  model.
+  \begin{itemize}
+    \item It is hypothesized that water and solute molecules partition into the
+    membrane and diffuse across the polymer matrix due to a chemical potential
+    gradient and then desorb into the permeate.
+    \item The product of a component's solubility and diffusivity is commonly
+    referred to as its permeability, $P$.~\cite{wijmans_solution-diffusion_1995}
+    \item $P$ is an intrinsic material property and is thus independent of membrane
+    thickness.  % BJC: is intensive a more appropriate word than intrinsic?
+    \item The water permeability coefficient \textit{is} dependent on thickness, $\delta_m$,
+    and can be formulated in terms of the pure water permeability, $P_w$.
+    \item \begin{equation}
+    A = \frac{P_wV_w}{\delta_mR_gT}
+    \end{equation}
+    where $V_w$ is molar volume of water, $R_g$ is the gas constant and $T$ is
+    absolute temperature.
+    \item Solute flux is modeled as:
+    \begin{equation}
+    J_s = \frac{P_s}{\delta_m}\Delta c_m = B\Delta c_m
+    \end{equation}
+    where B is a solute permeability coefficient and $\Delta c_m$ is the concentration
+    difference across the selective membrane layer.
+    \item Under these assumptions, rejection can be reformulated as
+    \begin{equation}
+    R = \frac{A}{A + B}
+    \end{equation}
+    which approaches unity as the solute flux tends towards zero.
+  \end{itemize}
+
+  These equations provide a somewhat limited perspective on the molecular details
+  of transport.
+  \begin{itemize}
+    \item The parameters are experimental observables which allow one to 
+    speculate on the atomic-level which cause them.
+    \item Further, this assumes that solutes undergo Brownian motion. As will
+    be discussed, solutes appear to undergo subdiffusive behavior on short
+    timescales. Therefore, we may need a more descriptive theory in order
+    to appropriately address questions of membrane design.
+  \end{itemize}
+
+  \subsection{Atomistic Molecular Simulation of LLC Membranes}
 
   %BJC: following two paragraphs taken from first paper.
+  %BJC2: Could probably reorganize the sentences of these next two paragraphs 
+  % to flow better with rest of intro.
   Our current understanding of the molecular details of LLC polymer membranes'
@@
     molecular-level solute transport and suggest governing mechanisms. 
-    \item We can also observe how the choice of head group interacts with solutes
-    of interest. 
-    \item In addition, we can interchange counterions which may influence both the pore size
-    and the strength of the Donnan potential.
+    \item We can also observe how the choice of head group and counterions interacts
+    with solutes of interest. 
   \end{itemize}
@@
     	\end{itemize}
-    \item Can we estimate experimentally-relevant macroscopic properties?
+    %MRS: maybe talk more about the stochastic modeling itself; for example, could phrase it in terms of
+    %how you can test mechanistic models to see if they are consistent with the timeseries, and then how those models
+    %can be further extrapolated to physical observables even if the MD simulations cannot. 
+    %MRS: this MIGHT include using the effective diffusion in a solution/diffusion model.
+    %\item Can we estimate experimentally-relevant macroscopic properties?
+    \item Can we formulate mechanistic models whose dynamical properties are consistent with our
+    molecular simulations and can be used to extrapolate macroscopic behavior which MD simulations cannot.
     	\begin{itemize}
@@
     	\end{itemize}
-    \item How can we learn mechanisms with minimal human intervention?  %BJC: i.e. machine learning methods
+
+    \item How can time series data directly inform us about transport mechanisms?
     	\begin{itemize}
@@
   \end{enumerate}
+
+  The next four chapters offer answers to each of the above questions and are adapted from 
+  various first author manuscripts at various stages in the publication process as described
+  below. The introduction to each adaptation is condensed in order to avoid redundancy and 
+  all other sections are left intact. The supporting information documents for each manuscript are
+  given in the appendices. \\
+
+  %BJC2: Should I just put title with reference? Or full citation?
+  \noindent\textit{Chapter 2}: adapted from manuscript entitled ``Understanding the 
+  Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes." 
+  published in the Journal of Physical Chemistry B.~\cite{coscia_understanding_2019} \\
+
+  \noindent\textit{Chapter 3}: adapted from manuscript entitled ``Chemically Selective 
+  Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane."
+  published in the Journal of Physical Chemistry B.~\cite{coscia_chemically_2019} \\
+
+  \noindent\textit{Chapter 4}: adapted from a manuscript in review with Physical Review E, entitled 
+  ``Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+  with Time Series Modeling". The final manuscript may change based on reviewer feedback. \\
+
+  \noindent\textit{Chapter 5}: adapted from the draft of a manuscript in preparation with the working
+  title ``Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
+  of Solute Trajectories in Nanostructured Membranes." The content will change as the
+  draft is finalized and after reviewer feedback.
+
+%  Chapter 2 is adapted 
+%  \begin{itemize}
+%    %BJC2: Should I just put title with reference? Or full citation?
+%    \item Chapter 2 is adapted from Coscia, B. J.; Yelk, J.; Glaser, M. A.; Gin, D. L.; Feng, X.; Shirts,
+%    M. R. Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer
+%    Membranes. J. Phys. Chem. B 2019, 123, 289-309.
+%    \item Chapter 3 is adapted Coscia and Shirts. Chemically Selective Transport in a Cross-Linked 
+%    H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane. J. Phys. Chem. B 2019, 123, 6314-6330. 
+%    \item Chapter 4 is adapted from a manuscript in review with Physical Review E, entitled 
+%    "Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+%    with Time Series Modeling". The final manuscript may change based on reviewer feedback.
+%    \item Chapter 5 is adapted from the draft of a manuscript in preparation with the working
+%    title "Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
+%    of Solute Trajectories in Nanostructured Membranes."
+%  \end{itemize}

### 2020-03-16 Ben_Manuscripts/thesis/intro.tex
Intro outline ready for a lookX

@@
     \item Untreated water can be a very complex solution with particles ranging
-    in size from microns down to nanometers
+    in size from microns down to nanometers.~\cite{goosen_fouling_2005}
     \item Sediment, bacteria, algae, proteins, small organic molecules, and ions
-    are all common components of aqueous streams.
+    are all common components of aqueous streams.~\cite{werber_materials_2016}
     \item The diversity in size and chemical topology of contaminants makes the
@@
     fouling, multiple types of membranes are often used in series, removing 
-    larger particles first.~\cite{goosen_fouling_2005}
+    larger particles first.~\cite{suk_membranebased_2006}
   \end{itemize}
@@
 
-  Membranes are generally designed to maximize two key performance metrics: 
-  permeability and selectivity.
+  Membranes are generally designed to optimize two key performance metrics: 
+  permeability and selectivity.~\cite{geise_water_2011}
+  %BJC2: Not sure the right place to put citation since its all described in the above citation. I could add more, but seems pointless.
   \begin{itemize}
@@
     only a small effect on energy requirements and capital costs. 
-    \item Cohen-Tanugi et al. calculated that tripling membrane permeability
-    could reduce energy consumption up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
+    \item Cohen-Tanugi \textit{et al.} calculated that a theoretical tripling of membrane permeability
+    would only reduce energy consumption by up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
     \item Perhaps the biggest detriment to energy consumption is the practical
-	need for multiple membrane passes in order to achieve a desired purity.
+	need for multiple membrane passes in order to achieve a desired purity.~\cite{singh_production_2009}
     \item Additionally, many membranes are not suited for high purity separations
     of small neutral species which necessitates chemical and capital costs for
-    post-treatment.
+    post-treatment.~\cite{shannon_science_2009,fritzmann_state---art_2007}
+%    \item The well-known permeability-selectivity tradeoff, common to dense polymer 
+%    membranes, directly correlates an increase in water permeability with an 
+%    increase in solute permeability.~\cite{geise_water_2011}
     \item Addressing these problems with highly selective separations may lead to 
-    more gains.
-    %MRS: math (or citations) for this statement?
+    more gains.~\cite{deshmukh_desalination_2015}
  \end{itemize}
@@
 
-  %BJC2: this section needs meat and citations
+  Selective separations are useful in a wide range of applications. They can be used
+  to separate components in both gaseous and aqueous phases.~\cite{baker_gas_2014}. We 
+  will focus this section on aqueous separations since they are the target process
+  for the following studies.
 
-  Selective separations are useful in a wide range of applications.
-
-  \textit{Desalination}:
-  Creating potable water from seawater or brackish water is of paramount importance
-  in water-scarce areas. 
+  \textit{Desalination}: Creating potable water from seawater or brackish water is of 
+  paramount importance in water-scarce areas. 
   \begin{itemize}
+    \item It is estimated that by 2025, 1.8 billion people may live in water-stressed
+    regions.~\cite{navarro-ortega_managing_2015} %There's a water stress index in fritzmann_2007
+    \item Membrane deslination via RO and thermal muli-stage flash distillation are 
+    both widely used processes for creating potable water in these regions.~\cite{fritzmann_state---art_2007}
   	\item Compared with thermal distillation techniques, RO has been shown to 
-  	be more environmently friendly and economical due to its lower energy
+  	be more environmentally friendly and economical due to its lower energy
   	requirements.\cite{morton_environmental_1997}
- 	\item In general, RO has a smaller footprint % BJC: need citation
-  	\item Thermal techniques are still preferred where excess waste heat or cheap 
+% 	\item In general, RO has a smaller footprint % BJC: need citation
+  	\item However, thermal techniques are still preferred where excess waste heat or cheap 
   	thermal energy is available, such as cogeneration plants.\cite{bhojwani_technology_2019}
@@
 
-  \textit{Organic Micropollutants}:
-  Municipal and industrial wastewaters are contaminated by harmful
+  \textit{Organic Micropollutants}: Municipal and industrial wastewaters are contaminated by harmful
   micropollutants, which can have adverse effects on human health even at low 
@@
     hormones, pesticides and industrial chemicals which find their way into
-    our drinking water supply.
+    our drinking water supply.~\cite{barbosa_occurrence_2016}
+    \item Sources of micropollutants incude industrial wastewater, 
+    agricultural runoff, landfill leachates and domestic effluents.~\cite{mompelat_occurrence_2009}
     %BJC2: There is a review I need to wade through to bulk this up.
-    \item Is there any infrastructure built to combat this?
+    \item Unfortunately, most waste water treatment plants are not 
+    designed for complete removal of these contaminants.~\cite{tijani_review_2013}
+    \item There is a need for a new generation of membranes that can better
+    target specific molecules.
   \end{itemize}
 
-  \textit{Recovery of Valuable Dissolved Species}: We can use highly selective
-  membranes in order to recover potentially valuable dissolved species from 
-  complex waste streams.
+  \textit{Recovery of Valuable Dissolved Species}: In addition to removing contaminants 
+  to clean waste water, we can also use highly selective membranes in order to recover
+  potentially valuable dissolved species from complex municipal and industrial waste
+  streams.~\cite{guest_new_2009,daigger_evolving_2009}
 
   Municipal waste-waters are rich in carbon, nitrogen and phosphorus-containing 
-  compounds. % i.e. poop
+  compounds.~\cite{romero_raw_2013}
   \begin{itemize}  
@@
   Industrial waste-waters are often quite complex with up to six times more 
-  total dissolved solids than seawater\cite{werber_materials_2016}. 
+  total dissolved solids than seawater.\cite{werber_materials_2016} 
   \begin{itemize}
@@
     shale formations consists of relatively high concentrations of salts, metals,
-    and soluble organic compounds. 
+    and soluble organic compounds.~\cite{orem_organic_2014}
     \item The majority of this water is disposed through deep well injection, 
@@
 
-  \textit{Breathable barriers}:
+%BJC: this is more of a gas separation
+%  \textit{Breathable barriers}:
+%  
+%  Finally, there is a great deal of military interest in creating breathable 
+%  barriers which selectively allow the passage of water in both directions but
+%  blocks out harmful contaminants.
+%  \begin{itemize}
+%    \item Need to allow sweating
+%    \item Can even put catalytic groups in the pores to break down contaminants
+%  \end{itemize}
 
-  Finally, there is a great deal of military interest in creating breathable 
-  barriers which selectively allow the passage of water in both directions but
-  blocks out harmful contaminants.
-  \begin{itemize}
-    \item Need to allow sweating
-    \item Can even put catalytic groups in the pores to break down contaminants
-  \end{itemize}
-
-  \section{Competing Membrane Technologies}
+  \section{Historical Development of Membrane Technology}
   %BJC2: maybe better to title this section "Historical Development of Membrane Technology"
@@
 
-  Nanofiltration membranes have pores on the order of 1 nm in size. Larger pore sizes 
-  allow lower operating pressures (3 -- 20 bar) which lowers energy consumption.~\cite{van_der_bruggen_review_2003}
-  An ideal NF membrane should have densely packed, uniform-sized and non-tortuous pores.
+  Since their introduction in the late 1980s, NF membranes have been applied towards
+  an increasing number of separations since they bridge the gap in capabilities
+  between reverse osmosis and ultrafiltration.~\cite{eriksson_nanofiltration_1988}
+  \begin{itemize}
+    \item Nanofiltration membranes have pores on the order of 1 nm in size. 
+    \item Larger pore sizes allow lower operating pressures (3 -- 20 bar) which lowers 
+    energy consumption.~\cite{van_der_bruggen_review_2003}
+    \item An ideal NF membrane should have densely packed, uniform-sized and non-tortuous pores.~\cite{jackson_nanoporous_2010}
     This combination has been practically difficult to realize.
+  \end{itemize}
 
@@
   \begin{itemize}
-    \item By modifying the monomer materials, one can control the structural morphology
-    produced by interfacial polymerization to create pores larger than those in RO
-    membranes.~\cite{seman_nanofiltration_2010}
+    \item NF membranes created by interfacial polymerization are made similarly to
+    RO membranes. By modifying the monomer materials, one can control the structural morphology
+    in order to create pores larger than those in RO membranes.~\cite{seman_nanofiltration_2010}
     \item During phase inversion, one submerges a polymer, dissolved in a solvent, in
@@
 
-  Track-etching is another technique which attempts to eliminate polydispersity and tortuosity.
-  During track-etching, a polymer film is bombarded with charged particles, then chemically 
-  etched to create pores.~\cite{apel_track_2001}
+  Track-etching is another NF fabrication technique which attempts to eliminate 
+  polydispersity and tortuosity. During track-etching, a polymer film is bombarded with 
+  charged particles, then chemically etched to create pores.~\cite{apel_track_2001}
   \begin{itemize}
-	\item Although the pores are uniform and non-tortuous, benefitting selectivity, the 
-	membranes have an extremely low pore density subsequently low permeability. 
+	\item Although the pores are uniform and non-tortuous, benefiting selectivity, the 
+	membranes have an extremely low pore density and subsequently low permeability. 
   \end{itemize}
-
-  %BJC2: maybe one more paragraph here with applications
 
@@
   % paragraphs.
-
-  Ultrathin-film graphene and graphene oxide membranes are an active area of research because
-  they are atomically thick materials and therefore offer potential for extremely high
-  permeability membranes.~\cite{humplik_nanostructured_2011} 
+  \textit{Graphene and graphene oxide} Ultrathin-film graphene and graphene oxide membranes
+  are an active area of research because they are atomically thick materials and therefore 
+  offer potential for extremely high permeability membranes.~\cite{humplik_nanostructured_2011} 
   \begin{itemize}
@@
 
-  Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
+  \textit{Carbon nanotubes}: Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
   due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011}
@@
     CNTs are extremely fast transporters of water.~\cite{hummer_water_2001,joseph_why_2008}
-    \item MD simulations by Kalra et al. predicted water transport at rates comparable
+    \item MD simulations by Kalra \textit{et al.} predicted water transport at rates comparable
     to the transmembrane protein aquaporin-1.~\cite{kalra_osmotic_2003}
@@
 
-  Zeolite membranes offer the potential for permeabilities comparable to ultrafiltration, 
+  \textit{Zeolites}: Zeolite membranes offer the potential for permeabilities comparable to ultrafiltration, 
   with selectivities as good as NF and RO.~\cite{hoek_nanotechnology-based_2014}
@@
 
-  Finally, metal organic frameworks (MOFs) have been recently introduced to the
-  field of aqueous separations.
+  \textit{Metal organic frameworks}: Finally, metal organic frameworks (MOFs) have been
+  recently introduced to the field of aqueous separations.
   \begin{itemize}
@@
   \begin{itemize}
-    \item Block copolymers
-    \item Some other amphiphilic self-assembled thing
-    \item Liquid crystals as the guy we are studying because we have lots of 
-    experimental data.
+    \item People are particularly interested in self-assembled materials because they
+    offer the potential of uniform-sized pores and tunable chemical and physical 
+    properties.~\cite{werber_materials_2016}
+    \item There are two major classes of self-assembled amphiphilic materials: block 
+    copolymers and liquid crystals.
   \end{itemize}
 
-  Under the right conditions, the shape and amphiphilic character of the monomers in 
-  Figure TBD drives their self assembly into ordered nanostructures.
+  Block copolymers contain more than one distinct repeating unit which facilitates 
+  the formation of self-assembled structures based on differences in the subunit 
+  amphiphilicity.~\cite{jackson_nanoporous_2010} 
   \begin{itemize}
-    \item Monomer 1 can form the inverted hexagonal phase (H\textsubscript{II})
-    \item Monomer 2 will form the bicontinuous cubic phase (Q\textsubscript{I})
-    \item The tails have vinyl groups which can be cross-linked for mechanical strength.
+%    \item The varying amphiphilic character of block copolymers, polymers with more than
+%    one distinct repeating unit, allows them to form self-assembled structures.~\cite{jackson_nanoporous_2010} 
+    \item Block copolymer membranes typically have pores on the order of 5-50 nm which
+    makes them useful for UF applications, however there is progress being made towards
+    smaller pores in the NF regime.~\cite{gu_tailoring_2015}
   \end{itemize}
 
-  %BJC: figure here showing each monomer and the phase they form
+  Under the right conditions, the shape and amphiphilic character of liquid 
+  crystal monomers drives their self-assembling into ordered nanostructures with
+  uniform-sized pores on the order of 1 nm in size.~\cite{gin_polymerized_2008}
+  \begin{itemize}
+    \item They have been used as membranes before.~\cite{gin_polymerized_2001}
+    \item As shown in Figure TBD, monomer 1 will form the inverted hexagonal phase 
+    (H\textsubscript{II})~\cite{smith_ordered_1997} while monomer 2 will form the 
+    bicontinuous cubic phase (Q\textsubscript{I})~\cite{carter_glycerol-based_2012}
+    \item The tails have vinyl groups which can be cross-linked for mechanical strength.
+    \item In this work we attempt to understand how one can design LLC membranes as 
+    alternative nanostructured materials for highly selective aqueous separations.
+    \item We chose to study liquid crystals because they are already suitable as NF 
+    membranes and there has been sufficient experimental characterization.~\cite{gin_polymerized_2001,feng_scalable_2014,feng_thin_2016}
+  \end{itemize}
 
-  In this work we attempt to understand how one can design LLC membranes as 
-  alternative nanostructured materials for highly selective aqueous separations.
+  %BJC: figure TBD here showing each monomer and the phase they form
 
@@
   The H\textsubscript{II} phase is characterized by hexagonally packed, uniform-sized
-  and straight pores.
+  and straight pores.~\cite{smith_ordered_1997}
   \begin{itemize}
@@
     \item Although the membranes have shown high experimental selectivity, their 
-    flux has been very low due to misalignment of the hexagonal mesophases.
+    flux has been very low due to misalignment of the hexagonal mesophases.~\cite{zhou_supported_2005}
   \end{itemize}
@@
   \begin{itemize}
-    \item Feng et al. leverage the magnetic anisotropy of the columnar \
+    \item Feng \textit{et al.} leveraged the magnetic anisotropy of the columnar
     mesophases in order to control their alignment with a magnetic field.~\cite{feng_scalable_2014}
-    \item Feng et al. also used an approach called soft confinement which
+    \item This study showed an 85-fold increase in ionic conductivity in the aligned
+    versus unaligned state, demonstrating a huge increase in feasibility as an industrial membrane.
+    \item Feng \textit{et al.} also used an approach called soft confinement which
     takes advantage of the hexagonal columns preference towards anchoring
     perpendicular to either a PDMS or glass substrate.~\cite{feng_thin_2016}
-    \item Finally, Feng et al. designed a third technique which uses a structure
+    \item Finally, Feng \textit{et al.} designed a third technique which uses a structure
     directing molecule in order to template the assembly of a fatty acid 
     molecule into ordered columnar phases.~\cite{feng_highly_2017}
-    \item Aligned hexagonal phase membranes exhibited an 85 fold increase in 
-    ionic conductivity.~\cite{feng_scalable_2014}
+%    \item Aligned hexagonal phase membranes exhibited an 85 fold increase in 
+%    ionic conductivity.~\cite{feng_scalable_2014}
   \end{itemize}
@@
   of nanostructured phases characterized by a network of 3 dimensionally
-  interconnected pores.
+  interconnected pores.~\cite{hyde_bicontinuous_1996}
   \begin{itemize}
@@
     through Q\textsubscript{I} membranes, they are more practical to synthesize
-    because the mesophases do not require alignment. 
+    because the mesophases do not require alignment.~\cite{zhou_new_2007}
   \end{itemize}
@@
     the self-assembly of a gemini phosphonium monomer in water.~\cite{pindzola_cross-linked_2003}
-    \item Hatakeyama et al. improved the industrial viability of Q\textsubscript{I} 
+    \item Hatakeyama \textit{et al.} improved the industrial viability of Q\textsubscript{I} 
     phase membranes by using a gemini ammonium monomer which is both easier and cheaper
@@
 
-  %BJC2: add more citations
   \noindent Membrane permeation is the result of a chemical potential gradient, $\frac{d\mu_i}{dx}$.
@@
 	  where $L_i$ is a coefficient of proportionality.~\cite{wijmans_solution-diffusion_1995}
+	  \item $L_i$ is an intrinsic materials property dependent on ... % Wijman's doesn't say. I don't want to speculate. Get book he referenced from library
       %MRS2: mention what L depends on molecularly (even if uncalculatable)
@@
 	  temperature and electromotive forces.
-	  \item We will limit our discussion to concentration and pressure gradients. %MRS: mention why?
+	  \item We will limit our discussion to concentration and pressure gradients because 
+	  these are primarily forces used for separations with the types of membranes we 
+	  will be studying.
   \end{itemize}
@@
   $\Delta P$ is the applied hydraulic pressure and $\Delta \pi_m$ is the 
-  trans-membrane osmotic pressure difference. The water permeability coefficient
-  is dependent on how one models flow through the membrane.
+  trans-membrane osmotic pressure difference. Estimates of the water permeability 
+  coefficient and the solute flux are dependent on how one models flow through the 
+  membrane.
 
@@
   %MRS: is this theory inadequate?  Will it be tested?
-  In porous membrane architectures, water flux is modeled as laminar flow through 
+  In porous membrane architectures, water and solute flux are modeled as laminar flow through 
   cylindrical pores.
@@
     \item The derivation follows Hagen-Poiseuille flow with inclusion of morphological
-    characteristics:
+    characteristics:~\cite{baker_membrane_2012}
     \begin{equation}
@@
     membrane thickness, and $\mu$ the solution viscosity.
-    \item Separation is typically characterized in terms of solute rejection, $R$. 
+    \item Solute flux, $J_s$ is related to $J_w$ but scaled by the empirically measured
+    permeate concentration:
+    \begin{equation}
+    J_s = c_p J_w
+    \end{equation}
+    \item Analytical expressions for solute flux, such as the Donnan Steric Pore Model (DSPM), 
+    are typically quite complicated because they attempt to incorporate more system features
+    leading to less assumptions.~\cite{bowen_modelling_2002}
+  \end{itemize}
+
+  Solute rejection is the quantity typically used to characterize the performance of a 
+  filtration membrane.
+  \begin{itemize}
+    \item Under the pore flow model, solutes with radii smaller than the pore will not 
+    pass through the membrane. 
+    \item A membrane with uniform-sized pores smaller than the solute being targeted 
+    for separation should have a solute flux of 0. However, in practice, most membranes
+    have a distribution of pore sizes, some large enough to allow solutes to pass.
+    \item Therefore, separation performance is typically characterized in terms of solute
+    rejection, $R$. 
     \begin{equation}
@@
     the permeate and feed respectively.
-    \item Solutes with radii smaller than the pore will be rejected. A distribution of 
-    pore sizes prevents perfect rejection.
+    \item The DSPM has been used to directly predict rejection.~\cite{hatakeyama_water_2011,bowen_modelling_2002}
   \end{itemize}
@@
     thickness.  % BJC: is intensive a more appropriate word than intrinsic?
-    \item The water permeability coefficient \textit{is} dependent on thickness, $\delta_m$,
+    \item The water permeability coefficient, $A$, \textit{is} dependent on thickness, $\delta_m$,
     and can be formulated in terms of the pure water permeability, $P_w$.
@@
     \end{equation}
-    where $V_w$ is molar volume of water, $R_g$ is the gas constant and $T$ is
+    where $V_w$ is molar volume of water, $R_g$ is the universal gas constant and $T$ is
     absolute temperature.
@@
     \end{equation}
-    where B is a solute permeability coefficient and $\Delta c_m$ is the concentration
-    difference across the selective membrane layer.
+    where $B$ is a solute permeability coefficient and $\Delta c_m$ is the concentration
+    difference across the selective membrane layer.~\cite{geise_fundamental_2014}
     \item Under these assumptions, rejection can be reformulated as
@@
     \end{equation}
-    which approaches unity as the solute flux tends towards zero.
+    which approaches unity as the solute flux tends towards zero.~\cite{van_der_bruggen_review_2003}
   \end{itemize}
@@
   \begin{itemize}
-    \item The parameters are experimental observables which allow one to 
-    speculate on the atomic-level which cause them.
-    \item Further, this assumes that solutes undergo Brownian motion. As will
+    \item The pore flow model neglects molecular level interactions with the membrane
+    and assumes all transport occurs within the cylindrical pore region. In this work, we
+    will show that solutes are not confined to the ``pore region" and that motion is 
+    heavily influenced by interactions with membrane.
+    \item The solution-diffusion model assumes that solutes undergo Brownian motion. As will
     be discussed, solutes appear to undergo subdiffusive behavior on short
-    timescales. Therefore, we may need a more descriptive theory in order
+    timescales. 
+    \item Therefore, we may need a more descriptive theory in order
     to appropriately address questions of membrane design.
+%    \item The parameters are experimental observables which allow one to 
+%    speculate on the atomic-level which cause them.
   \end{itemize}
@@
   % to flow better with rest of intro.
-  Our current understanding of the molecular details of LLC polymer membranes'
-  nanostructure is not sufficient to be able to precisely design them for
-  specific separations. Dischinger et al.~attempted to use an empirical model
-  that correlates the physiochemical properties of the counterion used in a
-  Q\textsubscript{I}-phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
-  Although their model showed some qualitative agreement with experiment, the
-  quality of fit of their model was limited due to complex solute-membrane
-  interactions that could not easily be modeled. Additionally, they observed
-  an unexpected discrepancy in the relationship between uncharged solute
-  rejection and water permeability, which will require a more in-depth knowledge of
-  the difference between solute and solvent transport.
-
-  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane
-  studies have been limited primarily to the Na-GA3C11 monomer with some
-  characterization done after minor structural modifications. For example, Resel
-  et al.~varied the length of the monomer tails and the counterion used and
-  observed its effect on pore spacing \cite{resel_structural_2000}. In a later
-  study of rejection performance, it was shown that membranes formed by
-  cross-linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes
-  less than 1.2 nm in diameter because the pores are too large
-  %MRS: this above is interesting, since that seems somewhat inconsistent with the 
-  \cite{zhou_supported_2005}. We do not yet understand how to controllably reduce
-  the effective pore size or how to tune the chemical environment in the
-  nanopores of this or related materials for small molecule separations. The only
-  source of predictive modeling for LLC systems have been macroscopic models that
-  likely do not adequately describe transport at these length scales
-  \cite{hatakeyama_water_2011}. Modeling with molecular detail could provide
-  sufficient information about the mechanisms and chemical features to better
-  inform experimental design of similar nanostructured membranes.
+  %BJC2: These next two paragraphs might function better in previous section.
+%  Our current understanding of the molecular details of LLC polymer membranes'
+%  nanostructure is not sufficient to be able to precisely design them for
+%  specific separations. Dischinger \textit{et al.}~attempted to use an empirical model
+%  that correlates the physiochemical properties of the counterion used in a
+%  Q\textsubscript{I}-phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
+%  Although their model showed some qualitative agreement with experiment, the
+%  quality of fit of their model was limited due to complex solute-membrane
+%  interactions that could not easily be modeled. Additionally, they observed
+%  an unexpected discrepancy in the relationship between uncharged solute
+%  rejection and water permeability, which will require a more in-depth knowledge of
+%  the difference between solute and solvent transport.
+%
+%  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane
+%  studies have been limited primarily to the Na-GA3C11 monomer with some
+%  characterization done after minor structural modifications. For example, Resel
+%  \textit{et al.}~varied the length of the monomer tails and the counterion used and
+%  observed its effect on pore spacing \cite{resel_structural_2000}. In a later
+%  study of rejection performance, it was shown that membranes formed by
+%  cross-linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes
+%  less than 1.2 nm in diameter because the pores are too large.
+%  %MRS: this above is interesting, since that seems somewhat inconsistent with the 
+%  \cite{zhou_supported_2005} We do not yet understand how to controllably reduce
+%  the effective pore size or how to tune the chemical environment in the
+%  nanopores of this or related materials for small molecule separations. The only
+%  source of predictive modeling for LLC systems have been macroscopic models that
+%  likely do not adequately describe transport at these length scales
+%  \cite{hatakeyama_water_2011}. Modeling with molecular detail could provide
+%  sufficient information about the mechanisms and chemical features to better
+%  inform experimental design of similar nanostructured membranes.
 
@@
   \begin{itemize}
-    \item Mondal et al. used MD simulations to study the self assembly of gemini 
+    \item Mondal \textit{et al.} used MD simulations to study the self assembly of gemini 
     surfactants and observed the formation of H\textsubscript{II} and Q\textsubscript{I}
     phases depending on water content.\cite{mondal_self-assembly_2013}
-    \item Mantha and Yethiraj as well as Roy et al. studied the dynamics of confined 
+    \item Mantha and Yethiraj as well as Roy \textit{et al.} studied the dynamics of confined 
     water in these systems and showed orders of magnitude differences in their motion
     dependent on system geometry.~\cite{mantha_dynamics_2016,roy_water_2016}
-    \item Jackson et al. as well as Mantha et al. have combined experiment with simulation
+    \item Jackson \textit{et al.} as well as Mantha \textit{et al.} have combined experiment with simulation
     in order to show how the choice of monomer head group counterion regulate water 
     dynamics.~\cite{jackson_ion-specific_2018,mantha_counterion-regulated_2018}
-    \item Sakamoto et al. and Nada et al. observed the dynamics of water molecules
+    \item Sakamoto \textit{et al}. and Nada \textit{et al}. observed the dynamics of water molecules
     and ions and hypothesized transport mechanisms in a simplified model of an LLC
@@
     %\item Can we estimate experimentally-relevant macroscopic properties?
+    %BJC2: modified thesis
     \item Can we formulate mechanistic models whose dynamical properties are consistent with our
@@
   The next four chapters offer answers to each of the above questions and are adapted from 
-  various first author manuscripts at various stages in the publication process as described
+  my first author manuscripts at various stages in the publication process as described
   below. The introduction to each adaptation is condensed in order to avoid redundancy and 

### 2020-03-19 Ben_Manuscripts/thesis/intro.tex
comments on intro.

@@
     would only reduce energy consumption by up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
+%MRS3: detriment -> impediment?
     \item Perhaps the biggest detriment to energy consumption is the practical
@@
   %BJC2: would a figure showing the nanostructures go well here? (a graphene film, a carbon nanotube, a MOF, a zeolite)
+  %MRS3: more figures almost always good.
 
@@
   % paragraphs.
-  \textit{Graphene and graphene oxide} Ultrathin-film graphene and graphene oxide membranes
+  \textit{Graphene and graphene oxide}: Ultrathin-film graphene and graphene oxide membranes
   are an active area of research because they are atomically thick materials and therefore 
@@
   \begin{itemize}
+%MRS3: tubular layers?
     \item CNTs are an allotrope of carbon consisting of tubular graphitic layers.~\cite{iijima_helical_1991}
@@
     \item The tails have vinyl groups which can be cross-linked for mechanical strength.
+%MRS3: Next bit seems a bit weird.
+If you making a transition to what you will be studying, it should be higher in indent level, since now you are switching to what you present.
+But if this is just a brief aside, maybe it should be left out, and then presented later?
     \item In this work we attempt to understand how one can design LLC membranes as 
     alternative nanostructured materials for highly selective aqueous separations.
+%MRS3: liquid crystal-based self-assembled nanostructures?  It's the structures that are of interest.
     \item We chose to study liquid crystals because they are already suitable as NF 
@@
     exhibit clear Ia3d symmetry.
+%MRS3: is this last bit necessarily implied (symmetry of phasae bby symmetry of salt)?  It's not clear to me it is.
   \end{itemize}
@@
   experiments that could be performed.
+
+  %MRS3: one issue is that after this paragraph, it's not entirely
+  %clear where you are going.  This describes common models, but not
+  %how your research is placed in respect to them.
 
@@
 
+%MRS3: think about if there is a way to better connect the information
+%above to the work carried out in the thesis, besides just ``we need a better theory''.
+
   \subsection{Atomistic Molecular Simulation of LLC Membranes}
@@
     	  \item After gaining a detailed picture of the nanopore structure, we can 
+%MRS: below: same, or qualitatively similar, or substantially similar? Think about a bit more. 
     	  feel confident that solutes in this system will experience the same 
@@
 
+  %MRS: maybe put supporting information for each chapter at the end of the chapter so it's in one place?
+
   %BJC2: Should I just put title with reference? Or full citation?
+  %MRS3: full citation.
   \noindent\textit{Chapter 2}: adapted from manuscript entitled ``Understanding the 

### 2020-03-20 Ben_Manuscripts/hdphmm/Outline.tex
Updated methods (pretty rough right now)

@@
   \maketitle
+
+  % BJC2: I'm not putting a lot of effort into the introduction since I'll only write
+  % an abbreviated form for my dissertation. I'll work on the intro after my defense.
 
@@
   We ran all MD simulations and energy minimizations using GROMACS 2018. We
-  performed all post-simulation trajectory using python scripts which are available
+  performed all post-simulation trajectory analysis using python scripts which are available
   online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
@@
   % described in our previous work..."
+  % BJC2: Or I could just say that I'm using the same data from the last paper. See that paper.
 
@@
   for modeling sequences of observations where the probability of the next observation
-  in a sequence depends on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
+  in a sequence depends, at least in, part on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
   %MRS2: it can depend on other things, but ALSO depends on the latent state.
+  %BJC2: added 'at least in part
   \begin{itemize}
@@
   % a reproduction of Fox et al's explanation: https://ieeexplore.ieee.org/abstract/document/5563110
+  % and it doesn't do a great job
   The infinite-state HMM overcomes this drawback by placing a hierarchical
@@
   %BJC: I do need to include this
-  \noindent We describe the dynamics of each state using a vector autoregressive (VAR) model. 
+  \noindent We describe the dynamics of each state using a first order vector autoregressive
+   (VAR(1)) model. 
   \begin{itemize}
-  	\item A VAR($r$) process is characterized by a vector of observations in a time series 
+  	\item In general, a VAR($r$) process is characterized by a vector of observations in a time series 
   	that are linearly dependent on $r$ previous values of the time series vector:
   	\begin{equation}
-  	\mathbf{y}_t = \mathbf{c} + \sum_{i=1}^r A_i\mathbf{y}_{t-i} + \mathbf{e}_t~~~~\mathbf{e}_t \sim N(0, \Sigma)
+  	\mathbf{y}_t = \mathbf{c} + \sum_{i=1}^r A_i\mathbf{y}_{t-i} + \mathbf{e}_t~~~~\mathbf{e}_t \sim \mathcal{N}(0, \Sigma)
+  	\label{eqn:var}
   	\end{equation}
@@
         %MRS2: mean is zero in Z, is it necessarily in R (I realize we've talked about this before, but wanted to get the clarification in text)
-  	\item We assumed multivariate Gaussian noise, with mean zero and covariance, $\Sigma$.
-  	\item We limited our analysis to an autoregressive order of $r=1$. %BJC: might try higher orders, but probably not worth it
+    %BJC2: The mean I'm talking about below is different than you are describing above.
+    % The multivariate Gausian noise is coming from N(0, \Sigma)
+  	\item We assumed $\mathbf{e}_t$ to be multivariate Gaussian noise, with mean zero and
+  	covariance, $\Sigma$.
+  	\item We limited our analysis to an autoregressive order of $r=1$.
   	\item We used a conjugate matrix-normal inverse-Wishart prior on parameters
@@
 
-  We applied the IHMM algorithm to the radial and axial coordinates of each 
-  solute center-of-mass trajectory.
+  There are many ways one can apply the IHMM algorithm to timeseries data. 
   \begin{itemize}
-    \item We measured the radial coordinate as the distance from the closest
-    pore center.
-    \item Because the pores are somewhat tortuous, we approximated the pore 
-    center with a spline. See previous work.
-    %MRS2: approximated the pore center line with a spline?
+    \item We begin by trying to identify as many distinct states as possible
+    in each solute trajectory and then take advantage of the system's cylindrical
+    symmetry in order to cluster the parameter sets into an interpretable number
+    of states.
+    \item Having a large number of states gives more reliable clustering results.
+%    \item We believe the subsequent procedure is best suited for our data
+%    because it can clearly distinguish different dynamical behavior, it takes
+%    advantage of the system's cylindrical symmetry and represents distinct
+%    dynamics in an interpretable number of states.
+  \end{itemize}
+
+  %BJC2: this is hard to word clearly. Maybe a small figure would help
+  We first applied the IHMM algorithm to the 3D solute center-of-mass coordinate 
+  trajectories transformed relative to the closest pore center.
+  \begin{itemize}
+    \item We tracked the solute's motion along the pore axis with center-of-mass
+    $z$ coordinate.
+    \item Using the nearest pore center as the origin, we represented the radial 
+    distance of each solute's center-of-mass from the pore center in 2 dimensions,
+    $x$ and $y$.
+    \item By using 2 dimensions, rather than a single radial dimension, we
+    increase the likelihood of finding more states since a single radial
+    mean can be represented by an infinite number of $x$ and $y$ coordinate combinations.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.2\textwidth]{cartesian_cylinder.pdf}
+  \caption{Using the nearest pore center as the origin, we represented the solute's
+  location along the pore axis in terms of the $z$ coordinates and their radial distance
+  from the pore centers in 2 dimensions, $x$ and $y$.}\label{fig:cartesian_cylinder}
+  \end{figure}
+
+  We applied the IHMM to each of the 24 solute trajectories independently.
+  \begin{itemize}
+    \item Although the IHMM is capable of identifying an infinite number of states, 
+    a Dirichlet Process tends to exhibit a ``rich get richer" effect, favoring
+    a fewer number of states.
+    \item By applying the algorithm to each trajectory independently we reduce
+    the possibility of lumping together multiple similar states which we
+    would prefer to stay separated before clustering.
+%    \item From a practical implementation standpoint, the algorithm is written
+%    such that we must put a cap on the maximum number of states. We chose to 
+%    allow up to 100 states for each trajectory although the algorithm typically
+%    finds within the range of 5-15 states. 
+    % BJC2: There will probably be a figure telling the number of states for 
+    % each trajectory.
+  \end{itemize}
+
+  The states predicted by the IHMM are heavily influenced by the Gaussian prior
+  placed on $c$ in Equation~\ref{eqn:var}.
+  \begin{itemize}
+    \item The $A$ and $\mathbf{e}_t$ matrices do not vary over a wide range, so
+    the final parameters were relatively insensitive to the priors.
+    \item In order to maximally automate the IHMM procedure, we attempted to
+    parameterize the prior on $c$ in an intelligent way.
+    \item The prior parameters should be chosen such that the means of 
+    each state lie within a region of reasonable probability of the prior (see
+    Figure~\ref{fig:prior_guesses}).
+    \item In each dimension, we defined the prior mean to be halfway between the 
+    maximum and minimum of each trajectory dimension. 
+    \item We defined the maximum and minimum to be 2 standard deviations from
+    the mean in order to parameterize the variance in each dimension.
+    \item Although this approach has worked quite well for the data in this work,
+    it is important to check the results to determine whether further adjustments
+    to the prior might be needed.
+    \item In the Supporting Information, we show the result of a parameterization
+    where the prior parameters of $c$ were poorly chosen.
+  \end{itemize}
+
+  %BJC2: I think it would be useful to continue using this trajectory to illustrate 
+  % the parameterization process. It might be bunch of plots stacked on each other.
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{prior_guesses.pdf}
+  \caption{The parameters of the prior on $c$ (black line) should be chosen such
+  that the means of each state identified in the trajectory (blue line) lie within
+  regions of the prior with reasonable probability. We chose the mean of the prior 
+  as halfway between the maximum and minimum of each trajectory dimension. We also
+  defined the maximum and minimum to be 2 standard deviations from the mean in 
+  order to parameterize $\sigma$.}\label{fig:prior_guesses}
+  \end{figure}
+
+  We ran 2000 iterations of the IHMM procedure in order to arrive at converged 
+  state sequence and parameters for each state.
+  \begin{itemize}  
+    \item Most parameters converged quickly (within 50-100 iterations) while
+    others took up to 1000 iterations.
+    \item We averaged the parameters from each iteration after the equilibration
+    time point.
+    \item We detected equilibration of the parameters using the module 
+    \texttt{pymbar.timeseries.detect\_equilibration} on the time series of 
+    parameter estimates. 
+    \item Since all of the parameters are multidimensional, we found the 
+    equilibration time point of each component and then used the longest
+    equilibration time of all dimensions as the equilibration time point.
+  \end{itemize}
+
+  % BJC2: It's probably possible to convert to from x, y, z to r, z but
+  % I need to figure out the transformation of A. This approach works though.
+  We reparameterized the time series, preserving the state sequence, in terms
+  of the radial and axial coordinates ($r$, $z$) because the mean in $r$ is 
+  a useful clustering variable.
+  \begin{itemize}
+    \item It will also be clearer to analyze the final parameter set in
+    terms of $r$ rather than $x$ and $y$.
+    \item We converted the $x$ and $y$ center-of-mass coordinates to $r$.
+    \item In order to keep the same states found by applying the algorithm
+    in 3D, we reapplied the IHMM to the cylindrical trajectories, only allowing
+    inference on the VAR(1) parameters with a fixed state sequence. 
   \end{itemize}
@@
   \begin{itemize}
-    %MRS2: can you enforce that the mean in the z-component is zero?
-    %MRS2: I'm trying to think what other constraints should be enforced. 
-    %MRS2: the issue with state clustering is that when transitionin between two states that are clustered, 
-    %MRS2: it destroys the correlation that would have been within if it was all the same statee.
-    %MRS2: I'm not sure what the implications are. If the simulations are RUN with grouped states, 
-    %MRS2: then the correlation can be reintroduced, so maybe it doesn't matter?
-   \item Since the mean vector, $\mathbf{c}$ of each state can take on 
-    continuous values, the IHMM algorithm tends to find a large number of states,
-    with very few states revisited.
-    % BJC1: This will need to be updated depending on how I cluster. Might need to describe
-    % multiple clustering approaches.
-    \item However, $\mathbf{A_i}$ and $\mathbf{\Sigma}$ tend to share similarities with
-    independently identified states. Therefore, we clustered based on $\mathbf{A_i}$
-    and $\mathbf{\Sigma}$, ignoring the mean.
-    \item Since  we do not know the number of similar states beforehand, we used
-    a non-parametric Bayesian Gaussian mixture model % cite scikit-learn
-    \item We used the clustered parameters in order to relabel states in the estimated
-    state sequences and to recalculate the state transition probability matrix.
+   \item For each solute studied, we identified between 200-300 independent sets of
+   parameters. % BJC2: just a guess for now
+   \item Many of these states exhibit very similar dynamical behavior except their
+   mean levels are different, especially in the axial direction where solutes could
+   get trapped along a broad and continuous range of $z$ coordinates.
+   \item Since we do not know the number of states with shared dynamical behavior
+   beforehand, we used a non-parametric Bayesian Gaussian mixture model in order
+   to group them. % cite scikit-learn  
+   \item This is necessary for us to perform any kind of mechanistic speculation.
   \end{itemize}
 
-  We generated stochastic trajectory realizations by drawing state sequences 
+  We clustered based on 5 variables: the radial means of each state, the two
+  eigenvalues of $A$ and the two eigenvalues of $e_t$.
+  \begin{itemize}
+   \item Unfortunately, the number of independent parameter sets is too low for
+   clustering in higher dimensions. 
+   \item Ideally, we could use all of the entries of $A$ and $e_t$ in addition to 
+   the radial means.
+   \item It would not be helpful to use the means in the $z$ direction because solutes
+   are essentially unbound in that direction, while there tends to be radially
+   dependent behavior as shown in our previous work.~\cite{coscia_chemically_2019}  % cite new paper too.
+  \end{itemize}
+
+  We remapped the state sequence based on the clustered assignments and
+  generated a state transition probability matrix, $T$.
+  \begin{itemize}
+   \item The IHMM algorithm also produces an estimate of $T$, but since we 
+   fixed the state sequence, we decided to explicitly calculate $T$ by 
+   counting the number of transitions between states.
+  \end{itemize}
+
+  We obtained clustered $\mathbf{c}$ vectors based on the means of 
+  $\mathbf{c}$ belonging to the same cluster.
+  \begin{itemize}
+   \item We only care about the $r$ component of $c$ because solute
+   trajectories are not boudn in the $z$ direction.
+  \end{itemize}
+
+  We used the IHMM algorithm in order to infer $A$ and $e_t$ of the 
+  clustered states.
+  \begin{itemize}
+   %BJC2: I'm unsure of the precise reasoning here.
+   \item We could not simply take the mean of the clustered 
+   $A$ and $e_t$ parameters because it is not clear that this is a linear 
+   operation for this problem. 
+   \item To circumvent this problem, we modified the ($r$, $z$) solute
+   trajectories so that they had a mean of zero, leaving only the 
+   fluctations. 
+   \item We did this by subtracting the maximum likelihood estimate
+   of the $\mathbf{c}$ vector from each same-state segement of the unclustered
+   trajectory.   
+   \item We used the IHMM algorithm on modified this modified trajectory to infer
+   the clustered state parameters by fixing the clustered state sequence. 
+  \end{itemize}
+
+  Finally, we generated stochastic trajectory realizations by drawing state sequences 
   based on the rows of $T$.

### 2020-03-23 Ben_Manuscripts/hdphmm/Outline.tex
Updates to methods

@@
   \subsection{The Infinite State Hidden Markov Model}\label{method:IHMM}
-  %BJC: There is a fair amount of detail here just so I could understand better by writing it out
 
@@
   for modeling sequences of observations where the probability of the next observation
-  in a sequence depends, at least in, part on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
+  in a sequence depends, at least in part, on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
   %MRS2: it can depend on other things, but ALSO depends on the latent state.
@@
     of observations.
-    \item Unfortunately, standard HMMs require the number of hidden states to be known
-    a priori.
+    \item The probability of transitioning to a state based on the current
+    state is mathematically defined in terms of an $n\times n$ transition
+    probability matrix, $T$, where $n$ is the number of states.
+    \item Unfortunately, standard HMMs require $n$ to be known
+    \textit{a priori}.
     \item One can partially overcome this by testing a range of numbers of 
@@
   % a reproduction of Fox et al's explanation: https://ieeexplore.ieee.org/abstract/document/5563110
-  % and it doesn't do a great job
   The infinite-state HMM overcomes this drawback by placing a hierarchical
@@
 
-  %BJC: I do need to include this
   \noindent We describe the dynamics of each state using a first order vector autoregressive
@@
   	\item We limited our analysis to an autoregressive order of $r=1$.
-  	\item We used a conjugate matrix-normal inverse-Wishart prior on parameters
-  	$A$ and $\Sigma$ and a conjugate Gaussian prior on $\mathbf{c}$ in order to analytically
-  	draw from the posterior.~\cite{fox_nonparametric_2009}
+  	\item We used a matrix-normal inverse-Wishart prior on parameters $A$ and $\Sigma$ 
+  	and a Gaussian prior on $\mathbf{c}$ in order to infer their values.~\cite{fox_nonparametric_2009}
+  	%BJC2: I'm not sure above is enough to make it clear how I got the parameters. Maybe I should
+  	% explicitly refer to the fox paper above which outlines the inference procedure in more detail?
   \end{itemize}
+
+  % BJC2: It might be useful to walk through the following procedure with an example 
+  % trajectory
 
@@
 
-  %BJC2: this is hard to word clearly. Maybe a small figure would help
-  We first applied the IHMM algorithm to the 3D solute center-of-mass coordinate 
+  We first applied the IHMM algorithm to 3D solute center-of-mass coordinate 
   trajectories transformed relative to the closest pore center.
   \begin{itemize}
-    \item We tracked the solute's motion along the pore axis with center-of-mass
+    \item We tracked the solute's motion along the pore axis with the center-of-mass
     $z$ coordinate.
@@
     distance of each solute's center-of-mass from the pore center in 2 dimensions,
-    $x$ and $y$.
+    $x$ and $y$ (see Figure~\ref{fig:cartesian_cylinder}).
     \item By using 2 dimensions, rather than a single radial dimension, we
@@
   \begin{itemize}
-    \item The $A$ and $\mathbf{e}_t$ matrices do not vary over a wide range, so
+    \item The entries of the $A$ and $\mathbf{e}_t$ matrices do not vary over a wide range, so
     the final parameters were relatively insensitive to the priors.
     \item In order to maximally automate the IHMM procedure, we attempted to
-    parameterize the prior on $c$ in an intelligent way.
+    parameterize the prior on $\mathbf{c}$ in an intelligent way.
     \item The prior parameters should be chosen such that the means of 
@@
     maximum and minimum of each trajectory dimension. 
-    \item We defined the maximum and minimum to be 2 standard deviations from
-    the mean in order to parameterize the variance in each dimension.
+    \item To parameterize the prior's variance in each dimension, we defined the maximum and minimum
+    to be 2 standard deviations from the mean.
     \item Although this approach has worked quite well for the data in this work,
@@
     \item In the Supporting Information, we show the result of a parameterization
-    where the prior parameters of $c$ were poorly chosen.
+    where the prior parameters of $c$ were poorly chosen. %TODO
   \end{itemize}
@@
   % the parameterization process. It might be bunch of plots stacked on each other.
+  %BJC2: More labels might be useful if not cluttered
   \begin{figure}
@@
   \caption{The parameters of the prior on $c$ (black line) should be chosen such
-  that the means of each state identified in the trajectory (blue line) lie within
+  that the mean levels of each state identified in the trajectory (blue line) lie within
   regions of the prior with reasonable probability. We chose the mean of the prior 
-  as halfway between the maximum and minimum of each trajectory dimension. We also
-  defined the maximum and minimum to be 2 standard deviations from the mean in 
-  order to parameterize $\sigma$.}\label{fig:prior_guesses}
+  as halfway between the maximum and minimum of each trajectory dimension. We chose 
+  $\sigma$ of the prior by defining the maximum and minimum to be 2 standard deviations
+  from the mean (dashed lines).}\label{fig:prior_guesses}
   \end{figure}
@@
   We ran 2000 iterations of the IHMM procedure in order to arrive at converged 
-  state sequence and parameters for each state.
+  state sequences and parameters for each state.
   \begin{itemize}  
@@
     others took up to 1000 iterations.
-    \item We averaged the parameters from each iteration after the equilibration
-    time point.
+    \item We averaged the parameters from each iteration recorded after the
+    equilibration time point.
     \item We detected equilibration of the parameters using the module 
@@
     \item We converted the $x$ and $y$ center-of-mass coordinates to $r$.
-    \item In order to keep the same states found by applying the algorithm
-    in 3D, we reapplied the IHMM to the cylindrical trajectories, only allowing
-    inference on the VAR(1) parameters with a fixed state sequence. 
+    \item In order to keep the same states found when we applied the algorithm
+    in 3D, we reapplied the IHMM to the cylindrical trajectories with a fixed 
+    state sequence, only allowing inference on the VAR(1) parameters. 
   \end{itemize}
@@
    to group them. % cite scikit-learn  
-   \item This is necessary for us to perform any kind of mechanistic speculation.
+%   \item This is necessary for us to perform any kind of mechanistic speculation.
   \end{itemize}
 
+  % BJC2: this part may expand a bit if I try different clustering approaches. But
+  % this is the one I'm going with for now.
   We clustered based on 5 variables: the radial means of each state, the two
@@
    \item It would not be helpful to use the means in the $z$ direction because solutes
-   are essentially unbound in that direction, while there tends to be radially
-   dependent behavior as shown in our previous work.~\cite{coscia_chemically_2019}  % cite new paper too.
+   are essentially unbound in that direction, while 
+   \item However, in our previous work, we observed radially dependent dynamical 
+   behavior.~\cite{coscia_chemically_2019}  % cite new paper too.
   \end{itemize}
 
-  We remapped the state sequence based on the clustered assignments and
+  We remapped the state sequence based on the cluster assignments and
   generated a state transition probability matrix, $T$.
@@
 
-  We obtained clustered $\mathbf{c}$ vectors based on the means of 
-  $\mathbf{c}$ belonging to the same cluster.
+  We obtained $\mathbf{c}$ vectors of the clustered states by averaging 
+  each value of $\mathbf{c}$ assigned to the same cluster.
   \begin{itemize}
-   \item We only care about the $r$ component of $c$ because solute
-   trajectories are not boudn in the $z$ direction.
+   \item We only care about the $r$ component of $\mathbf{c}$ because solute
+   trajectories are not bound in the $z$ direction.
   \end{itemize}
 
-  We used the IHMM algorithm in order to infer $A$ and $e_t$ of the 
+  We used the IHMM algorithm in order to infer $A$ and $\mathbf{e}_t$ of the 
   clustered states.
@@
    \item We could not simply take the mean of the clustered 
-   $A$ and $e_t$ parameters because it is not clear that this is a linear 
+   $A$ and $\mathbf{e}_t$ parameters because it is not clear that this is a linear 
    operation for this problem. 
@@
    trajectory.   
-   \item We used the IHMM algorithm on modified this modified trajectory to infer
+   \item We used the IHMM algorithm on this modified trajectory to infer
    the clustered state parameters by fixing the clustered state sequence. 
@@
 
-  Finally, we generated stochastic trajectory realizations by drawing state sequences 
-  based on the rows of $T$.
+  Finally, we generated stochastic trajectory realizations using the clustered
+  parameter sets.
   \begin{itemize}
+    \item We drew state sequences with transition probabilities weighted by the 
+    the rows of $T$.
     \item While in a given state, we simulated motion according to the VAR(1)
     parameterization of that state.
-    \item We set the unconditional mean of each state based on the position 
-    before the state transition occurred.
+    \item After each state transition, we reset the unconditional mean of each 
+    state based on the particle's position immediately before the state transition
+    occurred.
   \end{itemize}

### 2020-03-23 Ben_Manuscripts/hdphmm/Outline.tex
comments on 2.2

@@
     parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). 
-    \item The concentration parameter expresses one's confidence in H relative to the posterior 
+    %MRS3: This next line is a bit vauge (expresses confidence, closely related)
+   \item The concentration parameter $\gamma$ expresses one's confidence in H relative to the posterior 
     and is closely related to the number of data observations.
@@
     the MATLAB code of Fox et al.~\cite{fox_sticky_2007} 
+    %MRS3: be a bit more specific about what the criteria were for convergence.
     \item Parameter estimation is iterative. Therefore, we looked for convergence 
@@
     \item We refer the interested reader to much more extensive descriptions of 
+    %MRS3: be more specific about which parts from the above are in the references
     this process and its implementation. 
@@
 
+  %MRS3: be more specific - i.e. describe what are the ways you are going to apply it. 
   There are many ways one can apply the IHMM algorithm to timeseries data. 
   \begin{itemize}
+    %MRS3: it's not as many as possible, but identify one's supported by the data, right?
     \item We begin by trying to identify as many distinct states as possible
@@
     of states.
+    %MRS3: not clear why this is the case?
     \item Having a large number of states gives more reliable clustering results.
@@
     $x$ and $y$ (see Figure~\ref{fig:cartesian_cylinder}).
+    %MRS3: I'm not following the below? I don't know that we WANT to find more states, in my mind doing it this way 
+    %the math is simpler this way since we don't have to rewrite things in term of radial diffusion
+    %MRS3: we can brainstorm this as needed!
     \item By using 2 dimensions, rather than a single radial dimension, we
@@
   \centering
+  %MRS3: does this preserve the z-axis symmmetry? Is it just ensuring
+  %that you can't jump that far, or is it limitinig the values that
+  %the mean can take? Apologies if it's not clear to me yet.  I'm
+  %pretty sure it's just limiting the jump (since y_t = c + f(y_t-1)),
+  %but would be good to make that explicit - ``i.e. we need to make sure it doesn't jump too far'')
   \includegraphics[width=0.2\textwidth]{cartesian_cylinder.pdf}
@@
     \item To parameterize the prior's variance in each dimension, we defined the maximum and minimum
-    to be 2 standard deviations from the mean.
+    to be 2 standard deviations 
+    %MRS3: from the mean of what?
+    from the mean.
     \item Although this approach has worked quite well for the data in this work,
@@
   \begin{itemize}  
+    %MRS3: can you say more which categories converged quickly?
    \item Most parameters converged quickly (within 50-100 iterations) while
@@
     equilibration time point.
+    %MRS3: averaged and used this as estimate for running models later? 
+    %MRS3: other possbility is maximum a posteriori estimate, but for peaked symmetric distributions, it's essentially the same.
     \item We detected equilibration of the parameters using the module 
@@
     parameter estimates. 
+    %MRS3: not sure what you mean that they all were multidimensional?
     \item Since all of the parameters are multidimensional, we found the 
@@
   a useful clustering variable.
+  %MRS3: because of the radial symmetry, x and y aren't really meaningful alone. 
   \begin{itemize}
@@
     \item In order to keep the same states found when we applied the algorithm
-    in 3D, we reapplied the IHMM to the cylindrical trajectories with a fixed 
+    in 3D, 
+    %MRS3: would it be clearer to say you appplied only the inference part of the process on the clustered data?
+    we reapplied the IHMM to the cylindrical trajectories with a fixed 
     state sequence, only allowing inference on the VAR(1) parameters. 
+    %MRS3:did you cluster the state transitions as well? 
   \end{itemize}
@@
   \begin{itemize}
+  %MRS3: Maybe ``independent sets'' -> ``independent states, each with separate VAR(1) parameters?''
   \item For each solute studied, we identified between 200-300 independent sets of
@@
    beforehand, we used a non-parametric Bayesian Gaussian mixture model in order
+   %MRS3: group -> cluster
    to group them. % cite scikit-learn  
@@
    counting the number of transitions between states.
+   %MRS3: seems like you should just be able to lump together the IHMM states to generate the IHMM estimate of T?
   \end{itemize}
@@
 
+  %MRS3: ``used the IHMM algorithm'' -> ``used the parameter inference part of the IHMM algorithm''?
   We used the IHMM algorithm in order to infer $A$ and $\mathbf{e}_t$ of the 
@@
   \begin{itemize}
+    %MRS3: not sure what is meant by ``Weighted by the rows of T''? Should it just be given by T? 
     \item We drew state sequences with transition probabilities weighted by the 

### 2020-04-02 Ben_Manuscripts/hdphmm/Outline.tex
Calculate local density

@@
   in a sequence depends, at least in part, on a previous unobserved, latent or hidden, state.~\cite{beal_infinite_2002}
-  %MRS2: it can depend on other things, but ALSO depends on the latent state.
-  %BJC2: added 'at least in part
   \begin{itemize}
@@
   \begin{itemize}
-    \item Using some base probability distribution, H, a Dirichlet process 
-    (DP) generates distributions over a countably infinite number of 
-    probability measures:
+    \item Using some base probability distribution, $H$, a Dirichlet process 
+    (DP) generates discrete distributions, $G_0$, over a countably infinite 
+    number of probability measures:
     \begin{equation}
@@
     where the $\theta_k$ are values drawn from the base distribution and the
-    weights $\beta_k$ come from a stick-breaking process parameterized by the concentration 
-    parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). 
+    weights $\beta_k$ come from a stick-breaking process parameterized by the  
+    concentration parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). 
+    \item Also expressed $G_0 \sim DP(\gamma, H)$
     %MRS3: This next line is a bit vauge (expresses confidence, closely related)
-   \item The concentration parameter $\gamma$ expresses one's confidence in H relative to the posterior 
-    and is closely related to the number of data observations.
+    %BJC3: tried to make more clear
+    \item The concentration parameter, $\gamma$, expresses one's confidence in the 
+    base distribution $H$. 
+    \item When $\gamma\to 0$, the first weight of $G_0$, $\beta_1$, approaches 
+    unity and for $\gamma\to\infty$, the weights become uniform and $G_0$ closely
+    resembles $H$.
     \item Each row, $G_j$, of the transition matrix is produced by drawing from a DP specified 
@@
 
-  \noindent We describe the dynamics of each state using a first order vector autoregressive
-   (VAR(1)) model. 
+  We describe the dynamics of each state visited by solutes using a first order vector 
+  autoregressive (VAR(1)) model. 
   \begin{itemize}
@@
   	\end{equation}
-  	Previous observations are weighted by coefficient matrices $A_i$. The VAR($r$) 
+  	Previous observations are weighted by coefficient matrices, $A_i$. The VAR($r$) 
   	process is further characterized by a shift in the mean of each dimension by the
@@
   	\item We limited our analysis to an autoregressive order of $r=1$.
+  	\item This means that we only parameterize $A_1$. To simplify notation, we will just
+  	call it $A$.
   	\item We used a matrix-normal inverse-Wishart prior on parameters $A$ and $\Sigma$ 
@@
   %Based on the algorithms developed by Fox et al.~\cite{fox_sticky_2007}, 
-  Using the IHMM framework, we estimated the most likely number and sequence of hidden states
-  while simultaneously estimating VAR(1) parameters for each state and the overall 
-  state transition probability matrix, $T$.
+  Using the IHMM framework, we estimated the most likely number and sequence of hidden
+  states in each solute center-of-mass trajectory while simultaneously inferring VAR(1)
+  parameters for each state and the overall state transition probability matrix, $T$.
   \begin{itemize}
@@
     the MATLAB code of Fox et al.~\cite{fox_sticky_2007} 
+    %BJC3: I got the software from this page: https://homes.cs.washington.edu/~ebfox/software/
+    % Maybe I should reach out to emily fox to see how she would prefer I cite the software?
     %MRS3: be a bit more specific about what the criteria were for convergence.
+    %BJC3: See if that's better
     \item Parameter estimation is iterative. Therefore, we looked for convergence 
-    as shown in SI.
+    of each entry in the $c$ vector as well as the $A$ and $\Sigma$ matrices of 
+    Equation~\ref{eqn:var}.
+    \item Plots illustrating parameter convergence are available in the SI.
     \item We refer the interested reader to much more extensive descriptions of 
     %MRS3: be more specific about which parts from the above are in the references
-    this process and its implementation. 
+    %BJC3: made more specific
+    the inference and sampling procedures used to estimate the VAR(1) parameters
+    and the state sequence. 
     ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
@@
 
+  % BJC3: I tried again with this paragraph above. I want to set up the idea that we
+  % are performing this somewhat complex procedure for a good reason before jumping
+  % straight into it.
   %MRS3: be more specific - i.e. describe what are the ways you are going to apply it. 
-  There are many ways one can apply the IHMM algorithm to timeseries data. 
+%  There are many ways one can apply the IHMM algorithm to timeseries data. 
+%  \begin{itemize}
+%    %MRS3: it's not as many as possible, but identify one's supported by the data, right?
+%    \item We begin by trying to identify as many distinct states as possible
+%    in each solute trajectory and then take advantage of the system's cylindrical
+%    symmetry in order to cluster the parameter sets into an interpretable number
+%    of states.
+%    %MRS3: not clear why this is the case?
+%    \item Having a large number of states gives more reliable clustering results.
+%%    \item We believe the subsequent procedure is best suited for our data
+%%    because it can clearly distinguish different dynamical behavior, it takes
+%%    advantage of the system's cylindrical symmetry and represents distinct
+%%    dynamics in an interpretable number of states.
+%  \end{itemize}
+
+  We carefully applied the IHMM algorithm in a way which takes advantage of the
+  system's cylindrical symmetry.
   \begin{itemize}
-    %MRS3: it's not as many as possible, but identify one's supported by the data, right?
-    \item We begin by trying to identify as many distinct states as possible
-    in each solute trajectory and then take advantage of the system's cylindrical
-    symmetry in order to cluster the parameter sets into an interpretable number
-    of states.
-    %MRS3: not clear why this is the case?
-    \item Having a large number of states gives more reliable clustering results.
-%    \item We believe the subsequent procedure is best suited for our data
-%    because it can clearly distinguish different dynamical behavior, it takes
-%    advantage of the system's cylindrical symmetry and represents distinct
-%    dynamics in an interpretable number of states.
+%    \item In general we are interested in the time series created by tracing
+%    each solute's center of mass position. % ALready said this above
+    \item There are a number of viable ways in which one could choose to analyze 
+    these time series.
+    \item We could use all 3 dimensions straight from the output trajectory.
+    \item We could use just the $z$ dimensional coordinate since we are primarily
+    interested in through-plane membrane transport.
+    \item We chose to use a multi-step procedure that we believe adequately
+    distinguishes every type of distinct dynamical behavior exhibited by 
+    the solutes.
+    \item We work in cylindrical coordinates since each pore is cylindrical
+    and we expect solutes to exhibit radially symmetric dynamics.
   \end{itemize}
 
-  We first applied the IHMM algorithm to 3D solute center-of-mass coordinate 
+  We start by applying the IHMM algorithm to 3D solute center-of-mass coordinate 
   trajectories transformed relative to the closest pore center.
@@
     a fewer number of states.
-    \item By applying the algorithm to each trajectory independently we reduce
+    \item By applying the algorithm to each trajectory independently, we reduce
     the possibility of lumping together multiple similar states which we
@@
 
-  The states predicted by the IHMM are heavily influenced by the Gaussian prior
-  placed on $c$ in Equation~\ref{eqn:var}.
+  The states identified by the IHMM are heavily influenced by the Gaussian prior
+  placed on $\mathbf{c}$ in Equation~\ref{eqn:var}.
   \begin{itemize}
-    \item The entries of the $A$ and $\mathbf{e}_t$ matrices do not vary over a wide range, so
+    \item The entries of $A$ and $\Sigma$ do not vary over a wide range, so
     the final parameters were relatively insensitive to the priors.
@@
     Figure~\ref{fig:prior_guesses}).
-    \item In each dimension, we defined the prior mean to be halfway between the 
+    \item In each dimension, we defined the prior mean to lie halfway between the 
     maximum and minimum of each trajectory dimension. 
-    \item To parameterize the prior's variance in each dimension, we defined the maximum and minimum
-    to be 2 standard deviations 
-    %MRS3: from the mean of what?
-    from the mean.
+    \item To parameterize the prior's variance in each dimension, we defined the
+    maximum and minimum to be 2 standard deviations from the prior mean.
     \item Although this approach has worked quite well for the data in this work,
@@
     %MRS3: can you say more which categories converged quickly?
+    %BJC3: I imagine states with less sampling converge slower. But I'll need to
+    % look further into this.
    \item Most parameters converged quickly (within 50-100 iterations) while
     others took up to 1000 iterations.
-    \item We averaged the parameters from each iteration recorded after the
-    equilibration time point.
-    %MRS3: averaged and used this as estimate for running models later? 
-    %MRS3: other possbility is maximum a posteriori estimate, but for peaked symmetric distributions, it's essentially the same.
+    \item We defined the finalized parameters of each state as the average
+    of the parameters from each iteration recorded after the equilibration 
+    time point.
+    % MRS3: averaged and used this as estimate for running models later? 
+    % BJC3: yes, well for clustering. Tried to clarified above
+    % MRS3: other possbility is maximum a posteriori estimate, but for peaked 
+    % symmetric distributions, it's essentially the same.
     \item We detected equilibration of the parameters using the module 
@@
     parameter estimates. 
-    %MRS3: not sure what you mean that they all were multidimensional?
-    \item Since all of the parameters are multidimensional, we found the 
-    equilibration time point of each component and then used the longest
+    \item We found the equilibration time point of each component of the 
+    $\mathbf{c}$ vector as well as $A$ and $\Sigma$ matrices, and then used the longest
     equilibration time of all dimensions as the equilibration time point.
@@
   We reparameterized the time series, preserving the state sequence, in terms
-  of the radial and axial coordinates ($r$, $z$) because the mean in $r$ is 
-  a useful clustering variable.
-  %MRS3: because of the radial symmetry, x and y aren't really meaningful alone. 
+  of the radial and axial coordinates ($r$, $z$) because $x$ and $y$ aren't 
+  meaningful alone due to the system's radial symmetry.
+  % the mean in $r$ is a useful clustering variable.
   \begin{itemize}
@@
     \item We converted the $x$ and $y$ center-of-mass coordinates to $r$.
-    \item In order to keep the same states found when we applied the algorithm
-    in 3D, 
+%    \item In order to keep the same states found when we applied the algorithm
+%    in 3D, we reapplied the IHMM to the cylindrical trajectories with a fixed 
+%    state sequence, only allowing inference on the VAR(1) parameters.
     %MRS3: would it be clearer to say you appplied only the inference part of the process on the clustered data?
-    we reapplied the IHMM to the cylindrical trajectories with a fixed 
-    state sequence, only allowing inference on the VAR(1) parameters. 
-    %MRS3:did you cluster the state transitions as well? 
+    %BJC3: like this?
+    \item We fixed the state sequence from the 3D parmeterization and applied the
+    inference component of the IHMM procedure to the cylindrical trajectories in
+    order to estimate the VAR(1) parameters in terms of $r$ and $z$.
   \end{itemize}
@@
   \begin{itemize}
-  %MRS3: Maybe ``independent sets'' -> ``independent states, each with separate VAR(1) parameters?''
-  \item For each solute studied, we identified between 200-300 independent sets of
-   parameters. % BJC2: just a guess for now
+  \item For each solute studied, we identified 200-300 independent states, each
+  with separate VAR(1) parameters. % BJC2: just a guess for now
    \item Many of these states exhibit very similar dynamical behavior except their
@@
    beforehand, we used a non-parametric Bayesian Gaussian mixture model in order
-   %MRS3: group -> cluster
-   to group them. % cite scikit-learn  
+   to cluster them. % cite scikit-learn  
 %   \item This is necessary for us to perform any kind of mechanistic speculation.
@@
   We clustered based on 5 variables: the radial means of each state, the two
-  eigenvalues of $A$ and the two eigenvalues of $e_t$.
+  eigenvalues of $A$ and the two eigenvalues of $\Sigma$.
   \begin{itemize}
@@
    clustering in higher dimensions. 
-   \item Ideally, we could use all of the entries of $A$ and $e_t$ in addition to 
+   \item Ideally, we could use all of the entries of $A$ and $\Sigma$ in addition to 
    the radial means.
    \item It would not be helpful to use the means in the $z$ direction because solutes
-   are essentially unbound in that direction, while 
+   are essentially unbound in that direction.
    \item However, in our previous work, we observed radially dependent dynamical 
-   behavior.~\cite{coscia_chemically_2019}  % cite new paper too.
+   behavior.~\cite{coscia_chemically_2019}  % cite new paper eventually too.
   \end{itemize}
@@
    fixed the state sequence, we decided to explicitly calculate $T$ by 
-   counting the number of transitions between states.
+   counting the number of transitions between states compiled across all 
+   trajectories.
    %MRS3: seems like you should just be able to lump together the IHMM states to generate the IHMM estimate of T?
+   %BJC3: That's what I do. Maybe I'm misunderstanding your suggestion. I added a little bit to the sentence
+   % above to try and make more clear.
   \end{itemize}
@@
   %MRS3: ``used the IHMM algorithm'' -> ``used the parameter inference part of the IHMM algorithm''?
-  We used the IHMM algorithm in order to infer $A$ and $\mathbf{e}_t$ of the 
-  clustered states.
+  We used the parameter inference component of the IHMM algorithm in order to 
+  infer $A$ and $\Sigma$ of the clustered states.
   \begin{itemize}
@@
   \begin{itemize}
-    %MRS3: not sure what is meant by ``Weighted by the rows of T''? Should it just be given by T? 
-    \item We drew state sequences with transition probabilities weighted by the 
-    the rows of $T$.
+    \item We drew state sequences with transition probabilities given by $T$.
     \item While in a given state, we simulated motion according to the VAR(1)

### 2020-04-02 Ben_Manuscripts/thesis/intro.tex
Calculate local density

--- 2020-03-16 Ben_Manuscripts/thesis/intro.tex
@@
-\chapter{Introduction}\label{chapter:intro}
+8\chapter{Introduction}\label{chapter:intro}
 
@@
   Pressure driven membrane processes have become an increasingly useful tool for
-  performing aqueous separations.
-  \begin{itemize}
-    \item Untreated water can be a very complex solution with particles ranging
-    in size from microns down to nanometers.~\cite{goosen_fouling_2005}
-    \item Sediment, bacteria, algae, proteins, small organic molecules, and ions
+  performing aqueous separations. Untreated water can be a very complex solution
+  with particles ranging in size from microns down to nanometers.~\cite{goosen_fouling_2005}
+  Sediment, bacteria, algae, proteins, small organic molecules, and ions
   are all common components of aqueous streams.~\cite{werber_materials_2016}
-    \item The diversity in size and chemical topology of contaminants makes the
-    design of membrane processes meant to separate these components complex.
-    \item To deal with complex aqueous streams, and to prevent excessive membrane
-    fouling, multiple types of membranes are often used in series, removing 
-    larger particles first.~\cite{suk_membranebased_2006}
-  \end{itemize}
+  The diversity in size and chemical topology of contaminants makes the design of
+  membrane processes meant to separate these components complex. To deal with 
+  complex aqueous streams, and to prevent excessive membrane fouling, multiple 
+  types of membranes are often used in series, removing larger particles 
+  first.~\cite{suk_membranebased_2006}
 
-  % TFC membranes review -- "Composite reverse osmosis and nanofiltration membranes"
-  \noindent Modern membrane design is completely dependent on the target particle 
-  separation. 
-  \begin{itemize}
-    \item Separation membranes are most broadly classified based on the size of 
-    the particle they reject.
-    \item Microfiltration (MF) membranes contain pores with diameters ranging from 
-    100-10000 nm. They can separate large particles like bacteria and protozoa.~\cite{ma_functionalized_2014}
-    \item Ultrafiltration (UF) membranes have pore diameters of about 5-500 nm and are useful for the 
-    separation of sugars, proteins, viruses and colloidal materials.~\cite{yanful_ultrafiltration_2009}
-    \item Nanofiltration (NF) membranes have pores on the order of 1 nm in diameter and can 
+  Modern membrane design is completely dependent on the target particle 
+  separation. Separation membranes are most broadly classified based on the size of 
+  the particle they reject. Microfiltration (MF) membranes contain pores with 
+  diameters ranging from 100-10000 nm. They can separate large particles like 
+  bacteria and protozoa.~\cite{ma_functionalized_2014} Ultrafiltration (UF) 
+  membranes have pore diameters of about 5-500 nm and are useful for the separation
+  of sugars, proteins, viruses and colloidal materials.~\cite{yanful_ultrafiltration_2009}
+  Nanofiltration (NF) membranes have pores on the order of 1 nm in diameter and can 
   be used for the separation of small organic molecules and charged species.~\cite{van_der_bruggen_review_2003}
-    \item Reverse osmosis (RO) membranes are dense amorphous polymers with tortuous 
+  Reverse osmosis (RO) membranes are dense amorphous polymers with tortuous 
   pathways formed by collapsed polymer networks. Their dense polymer architecture 
   rejects all solutes to a high degree except for water making them useful for 
-    separating hydrated ions from water.~\cite{warsinger_review_2018}
-    \item We have summarized the uses of the different classes of membrane technologies in 
+  separating hydrated ions from water.~\cite{warsinger_review_2018} We have 
+  summarized the uses of the different classes of membrane technologies in 
   Figure~\ref{fig:size_regimes}.
-  \end{itemize}
 
@@
   Membranes are generally designed to optimize two key performance metrics: 
-  permeability and selectivity.~\cite{geise_water_2011}
-  %BJC2: Not sure the right place to put citation since its all described in the above citation. I could add more, but seems pointless.
-  \begin{itemize}
-    \item Permeability is used to quantify the rate at which solvent and solutes
-    pass through the membrane.
-    \item Selectivity quantifies the relative rates of passage of two substances.
-    \item A related quantity to selectivity, rejection, quantifies the fraction
+  permeability and selectivity.~\cite{geise_water_2011} Permeability is used to
+  quantify the rate at which solvent and solutes pass through the membrane.
+  Selectivity quantifies the relative rates of passage of two substances.
+  A related quantity to selectivity, rejection, quantifies the fraction
   of undesired solute that does not pass through the membrane.
-  \end{itemize}
 
@@
   selectivity may offer a more effective route towards lowering the cost of 
-  membrane separations.~\cite{werber_materials_2016}
-  \begin{itemize}
-    \item Increasing permeabilities beyond those already achieved may have 
-    only a small effect on energy requirements and capital costs. 
-    \item Cohen-Tanugi \textit{et al.} calculated that a theoretical tripling of membrane permeability
-    would only reduce energy consumption by up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
-    \item Perhaps the biggest detriment to energy consumption is the practical
+  membrane separations.~\cite{werber_materials_2016} Increasing permeabilities
+  beyond those already achieved may have only a small effect on energy 
+  requirements and capital costs. Cohen-Tanugi \textit{et al.} calculated that 
+  a theoretical tripling of membrane permeability would only reduce energy 
+  consumption by up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
+  Perhaps the most aggravating influence on energy consumption is the practical
   need for multiple membrane passes in order to achieve a desired purity.~\cite{singh_production_2009}
-    \item Additionally, many membranes are not suited for high purity separations
+  Additionally, many membranes are not suited for high purity separations
   of small neutral species which necessitates chemical and capital costs for
   post-treatment.~\cite{shannon_science_2009,fritzmann_state---art_2007}
-%    \item The well-known permeability-selectivity tradeoff, common to dense polymer 
-%    membranes, directly correlates an increase in water permeability with an 
-%    increase in solute permeability.~\cite{geise_water_2011}
-    \item Addressing these problems with highly selective separations may lead to 
-    more gains.~\cite{deshmukh_desalination_2015}
- \end{itemize}
+  Addressing these problems with highly selective separations may lead to 
+  more signficant advances.~\cite{deshmukh_desalination_2015}
 
@@
   will focus this section on aqueous separations since they are the target process
-  for the following studies.
+  for the studies that follow.
 
   \textit{Desalination}: Creating potable water from seawater or brackish water is of 
-  paramount importance in water-scarce areas. 
-  \begin{itemize}
-    \item It is estimated that by 2025, 1.8 billion people may live in water-stressed
-    regions.~\cite{navarro-ortega_managing_2015} %There's a water stress index in fritzmann_2007
-    \item Membrane deslination via RO and thermal muli-stage flash distillation are 
+  paramount importance in water-scarce areas. It is estimated that by 2025, 1.8 
+  billion people may live in water-stressed regions.~\cite{navarro-ortega_managing_2015} %There's a water stress index in fritzmann_2007
+  Membrane deslination via RO and thermal muli-stage flash distillation are 
   both widely used processes for creating potable water in these regions.~\cite{fritzmann_state---art_2007}
-  	\item Compared with thermal distillation techniques, RO has been shown to 
+  Compared with thermal distillation techniques, RO has been shown to 
   be more environmentally friendly and economical due to its lower energy
-  	requirements.\cite{morton_environmental_1997}
-% 	\item In general, RO has a smaller footprint % BJC: need citation
-  	\item However, thermal techniques are still preferred where excess waste heat or cheap 
-  	thermal energy is available, such as cogeneration plants.\cite{bhojwani_technology_2019}
-  \end{itemize}
+  requirements.\cite{morton_environmental_1997} However, thermal techniques are still
+  preferred where excess waste heat or cheap thermal energy is available, such as
+  cogeneration plants.\cite{bhojwani_technology_2019}
 
-  \textit{Organic Micropollutants}: Municipal and industrial wastewaters are contaminated by harmful
-  micropollutants, which can have adverse effects on human health even at low 
-  concentrations.\cite{schwarzenbach_challenge_2006}
-  \begin{itemize}
-    \item Micropollutants include pharmaceuticals, personal care products, 
-    hormones, pesticides and industrial chemicals which find their way into
-    our drinking water supply.~\cite{barbosa_occurrence_2016}
-    \item Sources of micropollutants incude industrial wastewater, 
-    agricultural runoff, landfill leachates and domestic effluents.~\cite{mompelat_occurrence_2009}
-    %BJC2: There is a review I need to wade through to bulk this up.
-    \item Unfortunately, most waste water treatment plants are not 
-    designed for complete removal of these contaminants.~\cite{tijani_review_2013}
-    \item There is a need for a new generation of membranes that can better
-    target specific molecules.
-  \end{itemize}
+  \textit{Organic Micropollutants}: Municipal and industrial wastewaters are contaminated
+  by harmful micropollutants, which can have adverse effects on human health even at low 
+  concentrations.\cite{schwarzenbach_challenge_2006} Micropollutants include pharmaceuticals,
+  personal care products, hormones, pesticides and industrial chemicals which find their way
+  into our drinking water supply.~\cite{barbosa_occurrence_2016} Sources of micropollutants
+  incude industrial wastewater, agricultural runoff, landfill leachates and domestic 
+  effluents.~\cite{mompelat_occurrence_2009} Unfortunately, most waste water treatment 
+  plants are not designed for complete removal of these contaminants.~\cite{tijani_review_2013}
+  There is a need for a new generation of membranes that can better target specific molecules.
 
@@
   Municipal waste-waters are rich in carbon, nitrogen and phosphorus-containing 
-  compounds.~\cite{romero_raw_2013}
-  \begin{itemize}  
-    \item The recovery of such products, which can be achieved using a 
-    selective membrane, has numerous potential uses.\cite{sales_resource_2015}
-    \item For example, nitrogen and phosphorus recovery can help sustain fertilizer 
+  compounds.~\cite{romero_raw_2013} The recovery of such products, which can be 
+  achieved using selective membranes, has numerous potential uses.\cite{sales_resource_2015}
+  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
   production which will help meet global food demand as population continues
   to increase.\cite{xie_membrane-based_2016}
-  \end{itemize}
 
   Industrial waste-waters are often quite complex with up to six times more 
-  total dissolved solids than seawater.\cite{werber_materials_2016} 
-  \begin{itemize}
-    \item For example, flowback water, produced during hydraulic fracturing of
-    shale formations consists of relatively high concentrations of salts, metals,
-    and soluble organic compounds.~\cite{orem_organic_2014}
-    \item The majority of this water is disposed through deep well injection, 
-    however there is a growing public concern about its management which has 
-    prompted the use of separation technologies such as RO and NF in order to 
-    reduce the volume of contaminated water.~\cite{gregory_water_2011}
-    \item Some of the dissolved organic compounds in flowback water, such as acetate, 
+  total dissolved solids than seawater.\cite{werber_materials_2016} For example,
+  flowback water, produced during hydraulic fracturing of shale formations consists
+  of relatively high concentrations of salts, metals, and soluble organic 
+  compounds.~\cite{orem_organic_2014} The majority of this water is disposed 
+  through deep well injection, however there is a growing public concern about
+  its management which has prompted the use of separation technologies such as 
+  RO and NF in order to reduce the volume of contaminated water.~\cite{gregory_water_2011}
+  Some of the dissolved organic compounds in flowback water, such as acetate, 
   are potentially valuable and can be recovered with highly selective membranes
   \cite{dischinger_application_2017}.
-  \end{itemize}
-
-%BJC: this is more of a gas separation
-%  \textit{Breathable barriers}:
-%  
-%  Finally, there is a great deal of military interest in creating breathable 
-%  barriers which selectively allow the passage of water in both directions but
-%  blocks out harmful contaminants.
-%  \begin{itemize}
-%    \item Need to allow sweating
-%    \item Can even put catalytic groups in the pores to break down contaminants
-%  \end{itemize}
 
   \section{Historical Development of Membrane Technology}
-  %BJC2: maybe better to title this section "Historical Development of Membrane Technology"
 
-  Membranes for separations are a relatively young technology. Over the past 60 years, 
-  the field has grown into a commercially viable technology and the focus has shifted
-  primarily towards incremental improvements in performance and most importantly,
-  targeted separations. This section will briefly cover a subset of the most relevant
-  membrane technologies which have ultimately inspired this thesis.
+  Membranes for separations are a relatively young technology that has expanded
+  rapidly. Over the past 60 years, the field has grown into a commercially viable
+  technology and the focus has shifted primarily towards incremental improvements
+  in performance and most importantly, targeted separations. This section will 
+  briefly cover a subset of the most relevant membrane technologies which have 
+  ultimately inspired this thesis.
 
@@
   in the 1960s and were made of the amorphous polymer cellulose acetate (CA).~\cite{kesting_semipermeable_1965}
-  \begin{itemize}
-    \item Reid and Spencer were among the first to show the ability of
-    these membranes to reject NaCl to high degrees ($\sim$ 99 \%) while subject 
-    to high applied pressures (270 atm).~\cite{reid_ultrafiltration_1960}
-    \item The most limiting drawback to CA membranes is their chemical instability, 
-    undergoing severe hydrolysis at pH values outside the range 4--6.~\cite{vos_kinetic_1966}
-  \end{itemize}
+  Reid and Spencer were among the first to show the ability of these membranes
+  to reject NaCl to high degrees ($\sim$ 99 \%) while subject to high applied 
+  pressures (270 atm).~\cite{reid_ultrafiltration_1960} The most limiting 
+  drawback to CA membranes is their chemical instability, undergoing severe 
+  hydrolysis at pH values outside the range 4--6.~\cite{vos_kinetic_1966}
 
   Amorphous thin film composite (TFC) polyamide membranes are the current industry 
-  standard for high purity RO separations.~\cite{baker_membrane_2012}
-  \begin{itemize}  
-    \item Developed in the 1980s, polyamide membranes are capable of rejecting salt
-    to a higher degree and can operate at wider pH ranges and higher feed pressures than 
-    CA membranes.~\cite{cadotte_interfacial_1981}
-    \item TFC polyamide membranes are typically formed by the interfacial polymerization
-    of a polyamide selective layer on the surface of a microporous polysulfone support 
-    layer.    
-    \item The support layer gives the membrane mechanical strength without hindering the
-    flow of water thereby permitting a very thin selective layer where molecular 
+  standard for high purity RO separations.~\cite{baker_membrane_2012} Developed 
+  in the 1980s, polyamide membranes are capable of rejecting salt to a higher 
+  degree and can operate at wider pH ranges and higher feed pressures than 
+  CA membranes.~\cite{cadotte_interfacial_1981} TFC polyamide membranes are 
+  typically formed by the interfacial polymerization of a polyamide selective 
+  layer on the surface of a microporous polysulfone support layer. The support
+  layer gives the membrane mechanical strength without hindering the flow of 
+  water thereby permitting a very thin selective layer where molecular 
   separations occur.~\cite{kucera_biofouling_2019}
-  \end{itemize}
 
@@
   in the range of 5 -- 120 bar, in order to achieve a useful permeate flux.~\cite{van_der_bruggen_review_2003}
-  \begin{itemize}
-    \item While the energy requirements to attain these pressures are still less than 
+  While the energy requirements to attain these pressures are still less than 
   the energy requirements of thermal distillation\cite{morton_environmental_1997}, it 
@@
     %BJC2: probably could use some citations here
-    \item It is not always necessary to achieve the high purity permeate streams
-    resulting from RO.
-    \item It is also possible that a target separation may be possible with 
-    membranes containing larger pores.
-    \item This has driven research into nanofiltration.
-  \end{itemize}
+  It is not always necessary to achieve the high purity permeate streams
+  resulting from RO. It is also possible that a target separation may be possible with 
+  membranes containing larger pores. This has driven research into nanofiltration.
 
@@
   between reverse osmosis and ultrafiltration.~\cite{eriksson_nanofiltration_1988}
-  \begin{itemize}
-    \item Nanofiltration membranes have pores on the order of 1 nm in size. 
-    \item Larger pore sizes allow lower operating pressures (3 -- 20 bar) which lowers 
-    energy consumption.~\cite{van_der_bruggen_review_2003}
-    \item An ideal NF membrane should have densely packed, uniform-sized and non-tortuous pores.~\cite{jackson_nanoporous_2010}
-    This combination has been practically difficult to realize.
-  \end{itemize}
+  Nanofiltration membranes have pores on the order of 1 nm in size. Larger pore sizes
+  allow lower operating pressures (3 -- 20 bar) which lowers energy consumption.~\cite{van_der_bruggen_review_2003}
+  An ideal NF membrane should have densely packed, uniform-sized and non-tortuous 
+  pores.~\cite{jackson_nanoporous_2010} This combination has been practically difficult to realize.
 
   The most widely used methods of NF membrane fabrication are interfacial polymerization
-  and phase inversion.
-  \begin{itemize}
-    \item NF membranes created by interfacial polymerization are made similarly to
-    RO membranes. By modifying the monomer materials, one can control the structural morphology
-    in order to create pores larger than those in RO membranes.~\cite{seman_nanofiltration_2010}
-    \item During phase inversion, one submerges a polymer, dissolved in a solvent, in
-    a non-solvent. A solid, porous polymer membrane is all that remains once all
-    solvent has been removed by non-solvent exchange.~\cite{smolders_microstructures_1992}
-    \item Although commercially dominant, both of these techniques suffer from
-    tortuous pores and polydisperse pore sizes which results in far from ideal 
-    selectivities.
-  \end{itemize}
+  and phase inversion. NF membranes created by interfacial polymerization are made similarly
+  to RO membranes. By modifying the monomer materials, one can control the resultant
+  membrane's structural morphology in order to create pores larger than those in RO 
+  membranes.~\cite{seman_nanofiltration_2010} During phase inversion, one submerges a 
+  polymer, dissolved in a solvent, in a non-solvent. A solid, porous polymer membrane 
+  is all that remains once all solvent has been removed by non-solvent exchange.~\cite{smolders_microstructures_1992}
+  Although commercially dominant, both of these techniques suffer from tortuous pores
+  and polydisperse pore sizes which results in far from ideal selectivities.
 
@@
   charged particles, then chemically etched to create pores.~\cite{apel_track_2001}
-  \begin{itemize}
-	\item Although the pores are uniform and non-tortuous, benefiting selectivity, the 
+  Although the pores are uniform and non-tortuous, benefiting selectivity, the 
   membranes have an extremely low pore density and subsequently low permeability.
-  \end{itemize}
 
@@
 
-  %BJC2: would a figure showing the nanostructures go well here? (a graphene film, a carbon nanotube, a MOF, a zeolite)
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{figs/graphene.pdf}
+  \caption{graphene}\label{fig:graphene}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{figs/cnt.png}
+  \caption{carbon nanotube}\label{fig:cnt}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth} % https://america.iza-structure.org/IZA-SC/framework_3d.php?STC=LTA
+  \includegraphics[width=\textwidth]{figs/zeolite.png}
+  \caption{zeolite, ZK-4}\label{fig:zeolite}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{figs/mof.png}
+  \caption{metal organic framework, MOF-5}\label{fig:mof}
+  \end{subfigure}
+  \caption{(a) Pristine graphene (left) and graphene oxide (right) are atomically thick,
+  offering the potential for high permeabilities. (b) Carbon nanotubes exhibit extemely
+  fast water transport due to their hydrophobic interiors. (c) Zeolites, like ZK-4 
+  shown here, possess cage-like structures that can trap solutes. (d) Metal organic
+  frameworks are flexible, porous structures capable of selective adsorption. }\label{fig:nanostructured_materials}
+  \end{figure}
 
-  %BJC2: Each tecnhology below will likely have its own heading and be split into 2 or more 
-  % paragraphs.
-  \textit{Graphene and graphene oxide} Ultrathin-film graphene and graphene oxide membranes
+  \textit{Graphene and graphene oxide}: Ultrathin-film graphene and graphene oxide membranes
   are an active area of research because they are atomically thick materials and therefore 
   offer potential for extremely high permeability membranes.~\cite{humplik_nanostructured_2011} 
-  \begin{itemize}
-    \item The tightly packed aromatic network of $sp^2$ hybridized carbon atoms that 
-    make up graphene sheets precludes the passage of even the smallest monoatomic species, helium.~\cite{bunch_impermeable_2008}
-    \item Controllably-sized pores have been created in pristine graphene by plasma etching
+  The tightly packed aromatic network of $sp^2$ hybridized carbon atoms that make up 
+  graphene sheets precludes the passage of even the smallest monoatomic species, helium.~\cite{bunch_impermeable_2008}
+  Controllably-sized pores have been created in pristine graphene by plasma etching
   and by charged particle bombardment.~\cite{surwade_water_2015,russo_atom-by-atom_2012}
-    \item Graphene oxide (GO), a highly oxidized modification of graphene, consist of epoxy,
+  Graphene oxide (GO), a highly oxidized modification of graphene, consist of epoxy,
   hydroxyl and carboxylate functional groups.~\cite{hegab_graphene_2015}
-    \item Many groups study GO membranes because they have improved antibacterial properties 
+  Many groups study GO membranes because they have improved antibacterial properties 
   over graphene, leading to less membrane fouling, and because their functionality can be
   modified in order to achieve solute-specific separations.~\cite{liu_antibacterial_2011,he_bioinspired_2013}
-    \item Despite their promise, scalable synthesis of monolayer graphene and GO membranes without
-    introducing microscopic, performance degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
-    \item Multilayered GO membranes have shown considerably more progress since their 
-    synthesis procedures are low cost and scalable.~\cite{zhang_size-controlled_2009}
-    \item GO sheets are particularly easy to make into multilayered membranes since they 
-    stack on top of each other, held together by hydrogen bonds.~\cite{homaeigohar_graphene_2017}
-    \item The potential of graphene and GO membrane certainly merits their continued exploration. Many
-    groups are still working in order to work on better control and standardization of their synthesis,
-    improving their designability for specific separations, and further improving their scalability.~\cite{wei_multilayered_2018}
-  \end{itemize}
 
-  \textit{Carbon nanotubes}: Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
-  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011}
-  \begin{itemize}
-    \item CNTs are an allotrope of carbon consisting of tubular graphitic layers.~\cite{iijima_helical_1991}
-    \item One can control CNT diameters down to 0.5 nm in size which has inspired the
-    creation of CNT membranes for reverse osmosis applications.~\cite{sun_creating_2000}
-    \item Molecular dynamics simulations have predicted and experiments have confirmed that
+  Multilayered GO membranes have shown considerably more progress than their single-layered
+  counterparts because their synthesis procedures are low cost and scalable.~\cite{zhang_size-controlled_2009} 
+  Despite their promise, scalable synthesis of monolayer graphene and GO membranes without
+  introducing microscopic, performance degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018} GO sheets are particularly easy to make into 
+  multilayered membranes since they stack on top of each other,
+  held together by hydrogen bonds.~\cite{homaeigohar_graphene_2017} The potential of 
+  graphene and GO membrane certainly merits their continued exploration. Many groups are still
+  working in order to work on better control and standardization of their synthesis, improving
+  their designability for specific separations, and further improving their scalability.~\cite{wei_multilayered_2018}
+
+  \textit{Carbon nanotubes}: Carbon nanotubes (CNTs) have shown promise as aqueous 
+  separations membranes due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011}
+  CNTs are an allotrope of carbon consisting of nested graphitic cylinders.~\cite{iijima_helical_1991}
+  Functionalization of the CNT pore entrances can potentially lead to highly selective 
+  separations.~\cite{fornasiero_ion_2008} One can control CNT diameters down to 0.5 nm 
+  in size which has inspired the creation of CNT membranes for reverse osmosis 
+  applications.~\cite{sun_creating_2000}
+
+  Molecular dynamics simulations have predicted and experiments have confirmed that 
   CNTs are extremely fast transporters of water.~\cite{hummer_water_2001,joseph_why_2008}
-    \item MD simulations by Kalra \textit{et al.} predicted water transport at rates comparable
-    to the transmembrane protein aquaporin-1.~\cite{kalra_osmotic_2003}
-    \item Experiments have exhibited water transport rates orders of magnitude higher than 
-    predictions by continuum modeling.~\cite{holt_fast_2006}
-    \item This enhancement has been explained as a result of nearly friction-less single-file water
-    flow through the hydrophobic CNT interiors.~\cite{kalra_osmotic_2003}
-    \item Functionalization of the CNT pore entrances can potentially lead to highly selective separations.~\cite{fornasiero_ion_2008}
-	\item Practically, dispersing and aligning CNTs into a polymer matrix is extremely
+  MD simulations by Kalra \textit{et al.} predicted water transport at rates comparable
+  to the transmembrane protein aquaporin-1.~\cite{kalra_osmotic_2003} Experiments have 
+  exhibited water transport rates orders of magnitude higher than predictions by 
+  continuum modeling.~\cite{holt_fast_2006} This enhancement has been explained as a 
+  result of nearly friction-less single-file water flow through the hydrophobic CNT 
+  interiors.~\cite{kalra_osmotic_2003}
+
+  Practically, dispersing and aligning CNTs into a polymer matrix is extremely
   difficult because they tend to agglomerate due to van der Waals forces.~\cite{sahoo_polymer_2010}
-    \item Some work has been to functionalize the carbon nanotubes in order to better incorporate them,
-    however facile incorporation at scale remains a challenge yet to be overcome.~\cite{kim_polysulfone_2007}
-  \end{itemize}
+  Some work has been to functionalize the carbon nanotubes in order to better incorporate 
+  them, however facile incorporation at scale remains a challenge yet to be overcome.~\cite{kim_polysulfone_2007}
 
-  \textit{Zeolites}: Zeolite membranes offer the potential for permeabilities comparable to ultrafiltration, 
-  with selectivities as good as NF and RO.~\cite{hoek_nanotechnology-based_2014}
-  \begin{itemize}  
-    \item Zeolites have highly uniform nm-sized crystalline structures with cage-like
-    cavities that allow movement and trapping of small solutes. 
-    \item The crystalline frameworks are typically formed by networks of silicon 
-    and aluminum each attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
-    \item One can replace the silicon and aluminum atoms via ion exchange in order
+  \textit{Zeolites}: Zeolite membranes offer the potential for permeabilities 
+  comparable to ultrafiltration, with selectivities as good as NF and RO.~\cite{hoek_nanotechnology-based_2014}
+  Zeolites have highly uniform nm-sized crystalline structures with cage-like
+  cavities that allow movement and trapping of small solutes. The crystalline 
+  frameworks are typically formed by networks of silicon and/or aluminum each 
+  attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
+  One can replace the silicon and aluminum atoms via ion exchange in order
   to control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}
-    \item Zeolite-coated ceramic membranes have shown the most promise for RO applications
+
+  A number of studies have tested the permeability and sodium salt rejection
+  of various zeolite membranes, however their high permeabilities typcially come
+  at the cost of low selectivities and vice versa.~\cite{li_desalination_2004,duke_seawater_2009}
+  Zeolite-coated ceramic membranes have shown the most promise for RO applications
   because of their mechanical stability under high applied pressure and chemical
   stability for withstanding disinfectants.~\cite{pendergast_review_2011}
-    \item A number of studies have tested the permeability and sodium salt rejection
-    of various zeolite membranes, however their high permeabilities typcially come
-    at the cost of low selectivities and vice versa.~\cite{li_desalination_2004,duke_seawater_2009}
-    \item Zeolites are also prone to defects in the crystalline structure which 
+  Unfortunately, zeolites are prone to defects in their crystalline structure which 
   would require substantial modification to the traditional synthesis procedures
   in order to fix.~\cite{kumakiri_application_2000}
-  \end{itemize}
 
   \textit{Metal organic frameworks}: Finally, metal organic frameworks (MOFs) have been
-  recently introduced to the field of aqueous separations.
-  \begin{itemize}
-    \item MOFs are highly porous and flexible crystalline structures made of metal
-    clusters coordinated to organic ligands.~\cite{furukawa_chemistry_2013}
-    \item There is a much wider breadth of research into MOFs as gas separation membranes
-    because they tend to be unstable in water.~\cite{feng_construction_2013}
-    \item But a new generation of water-stable MOFs is making it possible to use them
-    in aqueous separations.~\cite{wang_ultrastable_2015}
-    \item Purification of both aqueous and gaseous streams using MOFs are 
-    typically achieved by selective adsorption or catalytic degradation.~\cite{li_metalorganic_2012}    
-    \item MOFs have been applied towards the removal of a number of common water 
+  recently introduced to the field of aqueous separations. MOFs are highly porous and 
+  flexible crystalline structures made of metal clusters coordinated to organic 
+  ligands.~\cite{furukawa_chemistry_2013} Purification of waste streams using MOFs 
+  are typically achieved by selective adsorption or catalytic degradation.~\cite{li_metalorganic_2012}
+  There is a much wider breadth of research into MOFs as gas separation membranes 
+  because they tend to be unstable in water.~\cite{feng_construction_2013} But a new
+  generation of water-stable MOFs is making it possible to use them in 
+  aqueous separations.~\cite{wang_ultrastable_2015}
+
+  Recently, MOFs have been applied towards the removal of a number of common water 
   contaminants including dyes, pesticides, endocrine disruptors, and pharmaceuticals.
   \cite{zhang_fabrication_2015,seo_adsorptive_2015,li_metalorganic_2015,hasan_adsorptive_2012}
-    \item Although aqueous MOF separations are theorized to surpass the performance 
+  Although aqueous MOF separations are theorized to surpass the performance 
   of conventional membrane separations, it is still a budding field. The stability and
@@
   at scale.~\cite{dias_towards_2015}
-  \end{itemize}
 
@@
   Amphiphilic molecules that self-assemble to form ordered nanostructures have shown
-  potential as nanoporous membranes.
-  \begin{itemize}
-    \item People are particularly interested in self-assembled materials because they
-    offer the potential of uniform-sized pores and tunable chemical and physical 
-    properties.~\cite{werber_materials_2016}
-    \item There are two major classes of self-assembled amphiphilic materials: block 
-    copolymers and liquid crystals.
-  \end{itemize}
+  potential as nanoporous membranes. People are particularly interested in 
+  self-assembled materials because they offer the potential of uniform-sized pores
+  and tunable chemical and physical properties.~\cite{werber_materials_2016}
+  There are two major classes of self-assembled amphiphilic materials being studied
+  for separation applications: block copolymers and liquid crystals.
 
@@
   the formation of self-assembled structures based on differences in the subunit 
-  amphiphilicity.~\cite{jackson_nanoporous_2010} 
-  \begin{itemize}
-%    \item The varying amphiphilic character of block copolymers, polymers with more than
-%    one distinct repeating unit, allows them to form self-assembled structures.~\cite{jackson_nanoporous_2010} 
-    \item Block copolymer membranes typically have pores on the order of 5-50 nm which
-    makes them useful for UF applications, however there is progress being made towards
-    smaller pores in the NF regime.~\cite{gu_tailoring_2015}
-  \end{itemize}
+  amphiphilicity.~\cite{jackson_nanoporous_2010} Block copolymer membranes typically 
+  have pores on the order of 5-50 nm which makes them useful for UF applications, 
+  however there is progress being made towards smaller pores in the NF regime.~\cite{gu_tailoring_2015}
 
@@
   uniform-sized pores on the order of 1 nm in size.~\cite{gin_polymerized_2008}
-  \begin{itemize}
-    \item They have been used as membranes before.~\cite{gin_polymerized_2001}
-    \item As shown in Figure TBD, monomer 1 will form the inverted hexagonal phase 
+  As shown in Figure TBD, monomer 1 will form the inverted hexagonal phase 
   (H\textsubscript{II})~\cite{smith_ordered_1997} while monomer 2 will form the 
   bicontinuous cubic phase (Q\textsubscript{I})~\cite{carter_glycerol-based_2012}
-    \item The tails have vinyl groups which can be cross-linked for mechanical strength.
-    \item In this work we attempt to understand how one can design LLC membranes as 
-    alternative nanostructured materials for highly selective aqueous separations.
-    \item We chose to study liquid crystals because they are already suitable as NF 
-    membranes and there has been sufficient experimental characterization.~\cite{gin_polymerized_2001,feng_scalable_2014,feng_thin_2016}
-  \end{itemize}
+  The tails have vinyl groups which can be cross-linked for mechanical strength.
+
+  In this work we attempt to understand how one can design liquid crystal-based
+  self-assembled nanostructures for use as alternative membranes for highly selective 
+  aqueous separations. We chose to study liquid crystals because they are already 
+  suitable as NF membranes and there has been sufficient experimental 
+  characterization that we can use as benchmarks for our studies.~\cite{gin_polymerized_2001,feng_scalable_2014,feng_thin_2016}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/lc_phases.pdf}
+  \caption{}\label{fig:lc_phases}
+  \end{figure}
 
@@
   The H\textsubscript{II} phase is characterized by hexagonally packed, uniform-sized
-  and straight pores.~\cite{smith_ordered_1997}
-  \begin{itemize}
-    \item The hydrophilic head groups aggregate in the pore centers to create
-    cylindrical aqueous channels. 
-    \item These pore channels are lined with the chemical functionality of the LLC monomers
-    and have the potential to interact with solutes in a chemically-dependent manner.
-    \item The inhomogeneity of the pores suggests that the effective pore size may depend
-    on the solute. Both the size, shape and chemical functionality will influence
-    how a solute partitions within the membrane. %BJC2: need to rework this sentence.
-    \item In theory, this pore topology and geometry is ideal for high flux and 
+  and straight pores.~\cite{smith_ordered_1997} The hydrophilic head groups aggregate
+  in the pore centers to create cylindrical aqueous channels. These pore channels are
+  lined with the chemical functionality of the LLC monomers and have the potential to
+  interact with solutes in a chemically-dependent manner. The inhomogeneity of the 
+  pores suggests that the effective pore size may depend on the solute. Both the size,
+  shape and chemical functionality will influence how a solute partitions within the 
+  membrane. In theory, this pore topology and geometry is ideal for high flux and 
   highly selective separations.
-  \end{itemize}
 
@@
   mesophases into continuous pores that traverse the thickness of the membrane.
-  \begin{itemize}
-    \item Although the membranes have shown high experimental selectivity, their 
-    flux has been very low due to misalignment of the hexagonal mesophases.~\cite{zhou_supported_2005}
-  \end{itemize}
+  Although the membranes have shown high experimental selectivity, their flux has been
+  very low due to misalignment of the hexagonal mesophases.~\cite{zhou_supported_2005}
 
-%  Recently, Feng et al. has come up with two methods which can be used to 
-%  macroscopically align the hexagonal mesophases. 
   Considerable recent efforts have made progress towards the macroscopic
-  alignment of the hexagonal mesophases.
-  \begin{itemize}
-    \item Feng \textit{et al.} leveraged the magnetic anisotropy of the columnar
-    mesophases in order to control their alignment with a magnetic field.~\cite{feng_scalable_2014}
-    \item This study showed an 85-fold increase in ionic conductivity in the aligned
-    versus unaligned state, demonstrating a huge increase in feasibility as an industrial membrane.
-    \item Feng \textit{et al.} also used an approach called soft confinement which
-    takes advantage of the hexagonal columns preference towards anchoring
-    perpendicular to either a PDMS or glass substrate.~\cite{feng_thin_2016}
-    \item Finally, Feng \textit{et al.} designed a third technique which uses a structure
+  alignment of the hexagonal mesophases. Feng \textit{et al.} leveraged the magnetic 
+  anisotropy of the columnar mesophases in order to control their alignment with a 
+  magnetic field.~\cite{feng_scalable_2014} This study showed an 85-fold increase in
+  ionic conductivity in the aligned versus unaligned state, demonstrating a huge 
+  increase in feasibility as an industrial membrane. Feng \textit{et al.} also used
+  an approach called soft confinement which takes advantage of the hexagonal columns'
+  preference towards anchoring perpendicular to either a PDMS or glass substrate.~\cite{feng_thin_2016}
+  Finally, Feng \textit{et al.} designed a third technique which uses a structure
   directing molecule in order to template the assembly of a fatty acid 
-    molecule into ordered columnar phases.~\cite{feng_highly_2017}
-%    \item Aligned hexagonal phase membranes exhibited an 85 fold increase in 
-%    ionic conductivity.~\cite{feng_scalable_2014}
-  \end{itemize}
+  molecule into ordered columnar phases.~\cite{feng_highly_2017} These advances 
+  have revived research interest in H\textsubscript{II} phase membranes.
 
@@
 
-  The bicontinuous cubic, or Q\textsubscript{I} phase, is a class 
-  of nanostructured phases characterized by a network of 3 dimensionally
-  interconnected pores.~\cite{hyde_bicontinuous_1996}
-  \begin{itemize}
-    \item Aside from its tortuous pore architecture, it shares the 
-    uniform size and complex topological features of the H\textsubscript{II} phase
-    which lends itself to highly selective separations.
-    \item Although water and solutes must follow a longer path in order to pass
-    through Q\textsubscript{I} membranes, they are more practical to synthesize
-    because the mesophases do not require alignment.~\cite{zhou_new_2007}
-  \end{itemize}
+  The bicontinuous cubic, or Q\textsubscript{I} phase, is a class of nanostructured
+  phases characterized by a network of 3 dimensionally interconnected pores.~\cite{hyde_bicontinuous_1996}
+  Aside from its tortuous pore architecture, it shares the uniform size and complex 
+  topological features of the H\textsubscript{II} phase which lends itself to highly
+  selective separations. Although water and solutes must follow a longer path in order
+  to pass through Q\textsubscript{I} membranes, they are more practical to synthesize
+  than the H\textsubscript{II} phase because the mesophases do not require alignment.~\cite{zhou_new_2007}
+
+  % Figure here
 
   The space group of the Q\textsubscript{I} phase configuration formed by
-  monomer 1 is uncertain and thought to be either Pn3m or Ia3d.  %BJC: will have accompanying figure
-  \begin{itemize}
-    \item 6 Q phase architectures have been identified in small molecule
-    amphiphile systems.~\cite{mariani_cubic_1988}
-    \item Of these, only 4 are consistent with diffraction data generated
-    by the gemini surfactant used here.~\cite{pindzola_cross-linked_2003}
-    \item Q$^{230}$ (Ia3d), Q$^{224}$ (Pn3m), Q$^{229}$ (Im3m) or Q$^{212}$ (P4\textsubscript{3}32) phase of type I configuration
-    \item The presence of $1 / \sqrt{6}$ and $1 / \sqrt{8}$ peaks rules out the
-    Q$^{227}$ (Fd3m) and Q$^{223}$ (Pm3n) configurations.
-    \item The Pn3m and Ia3d architectures are the most common~\cite{mariani_cubic_1988,wiesenauer_nanoporous_2012}
-    \item The most likely phase is the type I Q$^{230}$ (Ia3d) because it is the
-    most common phase observed between lamellar and hexagonal phases and the
-    monomeric alkyltrimethylammonium salts used to synthesize the gemini LCs
-    exhibit clear Ia3d symmetry.
-  \end{itemize}
+  monomer 1 is uncertain and thought to be either Pn3m or Ia3d. Six Q phase
+  architectures have been identified in small molecule amphiphile systems.~\cite{mariani_cubic_1988}
+  Of these, only 4 are consistent with diffraction data generated by the gemini
+  surfactant used here: Q$^{230}$ (Ia3d), Q$^{224}$ (Pn3m), Q$^{229}$ (Im3m) and Q$^{212}$ 
+  (P4\textsubscript{3}32), all of type I configuration~\cite{pindzola_cross-linked_2003}
+  The presence of $1 / \sqrt{6}$ and $1 / \sqrt{8}$ peaks rules out the
+  Q$^{227}$ (Fd3m) and Q$^{223}$ (Pm3n) configurations. The Pn3m and Ia3d architectures
+  are most commonly observed experimentally.~\cite{mariani_cubic_1988,wiesenauer_nanoporous_2012}
+%    \item The most likely phase is the type I Q$^{230}$ (Ia3d) because it is the
+%    most common phase observed between lamellar and hexagonal phases and the
+%    monomeric alkyltrimethylammonium salts used to synthesize the gemini LCs
+%    exhibit clear Ia3d symmetry.
+%MRS3: is this last bit necessarily implied (symmetry of phasae bby symmetry of salt)?  It's not clear to me it is.
+%BJC3: Yea, I don't know, this was stated in a Gin paper
 
   Due to its more facile synthesis, there has been significantly more development
-  of Q\textsubscript{I} phase membranes.
-  \begin{itemize}
-    \item The first generation of Q\textsubscript{I} membranes was made by 
-    the self-assembly of a gemini phosphonium monomer in water.~\cite{pindzola_cross-linked_2003}
-    \item Hatakeyama \textit{et al.} improved the industrial viability of Q\textsubscript{I} 
-    phase membranes by using a gemini ammonium monomer which is both easier and cheaper
-    to synthesize.~\cite{hatakeyama_nanoporous_2010}
-    \item Free standing films of both first and second generation Q\textsubscript{I} phase 
-    membranes cannot withstand high pressure. Because solution casting was ineffective, Zhou
-    et. al used a hot-pressing method to make mechanically strong membranes which involves 
-    heating the initial monomer mixture to 70\degree C and pressing it with 12 tons of force
-    into a thick microporous, hydrophilic polymer support.~\cite{zhou_new_2007}
-    \item The most recent generation of Q\textsubscript{I} membranes uses an imidazolium-based
-    gemini LLC monomer which is capable of being solution cast into defect-free thin films on
-    porous supports. This improvement resulted in a ten-fold increase in flux while retaining
-    selectivities similar to earlier generations.~\cite{carter_glycerol-based_2012}
-  \end{itemize}
+  of Q\textsubscript{I} phase membranes. The first generation of Q\textsubscript{I}
+  membranes was made by the self-assembly of a gemini phosphonium monomer in 
+  water.~\cite{pindzola_cross-linked_2003} Hatakeyama \textit{et al.} improved the 
+  industrial viability of Q\textsubscript{I} phase membranes by using a gemini 
+  ammonium monomer which is both easier and cheaper to synthesize.~\cite{hatakeyama_nanoporous_2010}
+  Free standing films of both first and second generation Q\textsubscript{I} phase 
+  membranes cannot withstand high pressure. Because solution casting was ineffective,
+  Zhou et. al used a hot-pressing method to make mechanically strong membranes which
+  involves heating the initial monomer mixture to 70\degree C and pressing it with 12
+  tons of force into a thick microporous, hydrophilic polymer support.~\cite{zhou_new_2007}
+  The most recent generation of Q\textsubscript{I} membranes uses an imidazolium-based
+  gemini LLC monomer which is capable of being solution cast into defect-free thin films 
+  on porous supports. This improvement resulted in a ten-fold increase in flux while 
+  retaining selectivities similar to earlier generations.~\cite{carter_glycerol-based_2012}
 
@@
   State of the art Q\textsubscript{I} membranes offer selectivities that
-  are competitive with existing commercial technologies.
-  \begin{itemize}
-    \item When separating organic solutes from NaCl, Q\textsubscript{I}-phase
-    membrane filtration experiments have shown selectivity 2--3 times higher than
-    commercial RO and 6--12 times higher than commercial NF membranes
-    \cite{dischinger_application_2017}.
-    \item Water permeability is higher than commercial RO membranes but
-    less than commercial NF. There is work being done to reduce the
-    thickness of the selective layer in order to increase permeability. 
-  \end{itemize}
+  are competitive with existing commercial technologies. When separating organic
+  solutes from NaCl, Q\textsubscript{I}-phase membrane filtration experiments have
+  shown selectivity 2--3 times higher than commercial RO and 6--12 times higher 
+  than commercial NF membranes.~\cite{dischinger_application_2017} Their water 
+  lies between commercial RO and NF membranes. There is work being done to reduce 
+  the thickness of the selective layer in order to increase permeability.
 
@@
 
+  This thesis uses the high level of detail afforded by MD simulations in
+  order to understand solute transport within LLC membranes with molecular 
+  detail. Before diving into atomistic model, we offer a brief survey of 
+  the most popular macroscopic treatments in order to highlight how an
+  atomistic model may be better suited to understanding how to design LLC
+  %TODO
+
+  %MRS3: one issue is that after this paragraph, it's not entirely
+  %clear where you are going.  This describes common models, but not
+  %how your research is placed in respect to them.
+  %BJC3: Added above connecting paragraph
+
   \subsection{Macroscopic Treatments}
@@
 
-  \noindent Membrane permeation is the result of a chemical potential gradient, $\frac{d\mu_i}{dx}$.
-  \begin{itemize}
-	  \item The flux of component $i$ is proportional to this gradient:
+  Membrane permeation is the result of a chemical potential gradient, $\frac{d\mu_i}{dx}$.
+  The flux of component $i$ is proportional to this gradient:
   \begin{equation}
@@
   where $L_i$ is a coefficient of proportionality.~\cite{wijmans_solution-diffusion_1995}
-	  \item $L_i$ is an intrinsic materials property dependent on ... % Wijman's doesn't say. I don't want to speculate. Get book he referenced from library
+  $L_i$ is an intrinsic materials property dependent on ... % Wijman's doesn't say. I don't want to speculate. Get book he referenced from library
       %MRS2: mention what L depends on molecularly (even if uncalculatable)
-	  \item Chemical potential gradients can be induced by concentration, pressure, 
-	  temperature and electromotive forces.
-	  \item We will limit our discussion to concentration and pressure gradients because 
-	  these are primarily forces used for separations with the types of membranes we 
-	  will be studying.
-  \end{itemize}
+  Chemical potential gradients can be induced by concentration, pressure, temperature
+  and electromotive forces. We will limit our discussion to concentration and pressure
+  gradients because these are primarily forces used for separations with the types of 
+  membranes we will be studying.
 
-  %MRS: is there are reason you are talkling about just water flux here?
-  % This follows the discussion of werber_material_2016
-  %BJC2: add solute flux
   For pressure driven membrane processes, water flux through both porous and 
@@
 
-  %MRS: be clearer on presenting the context for this theory.  Will your findings be in contradiction?
-  %MRS: is this theory inadequate?  Will it be tested?
-  In porous membrane architectures, water and solute flux are modeled as laminar flow through 
-  cylindrical pores.
-  \begin{itemize}
-    \item The derivation follows Hagen-Poiseuille flow with inclusion of morphological
-    characteristics:~\cite{baker_membrane_2012}
+  In porous membrane architectures, water and solute flux are modeled as laminar flow
+  through cylindrical pores. The derivation of flux follows Hagen-Poiseuille flow with 
+  inclusion of morphological characteristics:~\cite{baker_membrane_2012}
   \begin{equation}
@@
   where $\varepsilon$ is the surface porosity, $r_p$ the pore radius, $\delta_m$ the
-    membrane thickness, and $\mu$ the solution viscosity.
-    \item Solute flux, $J_s$ is related to $J_w$ but scaled by the empirically measured
-    permeate concentration:
+  membrane thickness, and $\mu$ the solution viscosity. Solute flux, $J_s$ is related
+  to $J_w$ but scaled by the empirically measured permeate concentration:
   \begin{equation}
@@
   \end{equation}
-    \item Analytical expressions for solute flux, such as the Donnan Steric Pore Model (DSPM), 
+  Analytical expressions for solute flux, such as the Donnan Steric Pore Model (DSPM), 
   are typically quite complicated because they attempt to incorporate more system features
   leading to less assumptions.~\cite{bowen_modelling_2002}
-  \end{itemize}
 
-  Solute rejection is the quantity typically used to characterize the performance of a 
-  filtration membrane.
-  \begin{itemize}
-    \item Under the pore flow model, solutes with radii smaller than the pore will not 
-    pass through the membrane. 
-    \item A membrane with uniform-sized pores smaller than the solute being targeted 
-    for separation should have a solute flux of 0. However, in practice, most membranes
-    have a distribution of pore sizes, some large enough to allow solutes to pass.
-    \item Therefore, separation performance is typically characterized in terms of solute
-    rejection, $R$. 
+  Solute rejection is the quantity frequently used to characterize the performance of a 
+  filtration membrane. Under the pore flow model, solutes with radii smaller than the 
+  pore will not pass through the membrane. A membrane with uniform-sized pores smaller
+  than the solute being targeted for separation should have a solute flux of 0. However,
+  in practice, most membranes have a distribution of pore sizes, some large enough to
+  allow solutes to pass. Therefore, separation performance is typically characterized
+  in terms of solute rejection, $R$. 
   \begin{equation}
@@
   \end{equation}
-    where $c_p$ and $c_f$ are the concentrations of the rejected species in
-    the permeate and feed respectively.
-    \item The DSPM has been used to directly predict rejection.~\cite{hatakeyama_water_2011,bowen_modelling_2002}
-  \end{itemize}
+  where $c_p$ and $c_f$ are the concentrations of the rejected species in the permeate
+  and feed respectively. The DSPM has been used to directly predict 
+  rejection.~\cite{hatakeyama_water_2011,bowen_modelling_2002}
 
@@
   In amorphous membranes, water and solute flux are modeled using the solution-diffusion 
-  model.
-  \begin{itemize}
-    \item It is hypothesized that water and solute molecules partition into the
-    membrane and diffuse across the polymer matrix due to a chemical potential
-    gradient and then desorb into the permeate.
-    \item The product of a component's solubility and diffusivity is commonly
-    referred to as its permeability, $P$.~\cite{wijmans_solution-diffusion_1995}
-    \item $P$ is an intrinsic material property and is thus independent of membrane
-    thickness.  % BJC: is intensive a more appropriate word than intrinsic?
-    \item The water permeability coefficient, $A$, \textit{is} dependent on thickness, $\delta_m$,
+  model. It is hypothesized that water and solute molecules partition into the
+  membrane and diffuse across the polymer matrix due to a chemical potential gradient
+  and then desorb into the permeate. The product of a component's solubility and 
+  diffusivity is commonly referred to as its permeability, $P$.~\cite{wijmans_solution-diffusion_1995}
+  $P$ is an intrinsic material property and is thus independent of membrane thickness.  % BJC: is intensive a more appropriate word than intrinsic?
+  The water permeability coefficient, $A$, \textit{is} dependent on thickness, $\delta_m$,
   and can be formulated in terms of the pure water permeability, $P_w$.
-    \item \begin{equation}
+  \begin{equation}
     A = \frac{P_wV_w}{\delta_mR_gT}
@@
   where $V_w$ is molar volume of water, $R_g$ is the universal gas constant and $T$ is
-    absolute temperature.
-    \item Solute flux is modeled as:
+  absolute temperature. Solute flux is modeled as:
   \begin{equation}
@@
   difference across the selective membrane layer.~\cite{geise_fundamental_2014}
-    \item Under these assumptions, rejection can be reformulated as
+  Under these assumptions, rejection can be reformulated as
   \begin{equation}
@@
   which approaches unity as the solute flux tends towards zero.~\cite{van_der_bruggen_review_2003}
-  \end{itemize}
 
   These equations provide a somewhat limited perspective on the molecular details
-  of transport.
-  \begin{itemize}
-    \item The pore flow model neglects molecular level interactions with the membrane
-    and assumes all transport occurs within the cylindrical pore region. In this work, we
-    will show that solutes are not confined to the ``pore region" and that motion is 
-    heavily influenced by interactions with membrane.
-    \item The solution-diffusion model assumes that solutes undergo Brownian motion. As will
-    be discussed, solutes appear to undergo subdiffusive behavior on short
-    timescales. 
-    \item Therefore, we may need a more descriptive theory in order
-    to appropriately address questions of membrane design.
-%    \item The parameters are experimental observables which allow one to 
-%    speculate on the atomic-level which cause them.
-  \end{itemize}
+  of transport. The pore flow model neglects molecular level interactions with the 
+  membrane and assumes all transport occurs within the cylindrical pore region. In
+  this work, we will show that solutes are not confined to the ``pore region" and 
+  that motion is heavily influenced by interactions with membrane. The 
+  solution-diffusion model assumes that solutes undergo Brownian motion. As will
+  be discussed, solutes appear to undergo subdiffusive behavior on short timescales. 
+  Therefore, we may need a more descriptive theory in order to appropriately address
+  questions of membrane design.
+
+%MRS3: think about if there is a way to better connect the information
+%above to the work carried out in the thesis, besides just ``we need a better theory''.
 
@@
   A molecular-level understanding of the relationship between monomer structure
-  and solute transport can help provide guidelines to reduce the
-  large chemical space available to design monomers for creation of
-  separation-specific membranes.
-  \begin{itemize}
-    \item Atomistic MD simulations can provide the required level of detail 
-    (Figure \ref{fig:detailed_pore}), assuming the force fields are sufficiently accurate. 
-    \item With such an atomistic model, we can directly observe
-    molecular-level solute transport and suggest governing mechanisms. 
-    \item We can also observe how the choice of head group and counterions interacts
-    with solutes of interest. 
-  \end{itemize}
+  and solute transport can help provide guidelines to reduce the large chemical 
+  space available to design monomers for creation of separation-specific membranes. 
+  Atomistic MD simulations can provide the required level of detail (Figure 
+  \ref{fig:detailed_pore}), assuming the force fields are sufficiently accurate. 
+  With such an atomistic model, we can directly observe molecular-level solute 
+  transport and suggest governing mechanisms. We can also observe how the choice 
+  of head group and counterions interacts with solutes of interest.
 
@@
 
-  Although the Q\textsubscript{I} phase shows the most promise for
-  practical applications, the focus of this work will be on the H\textsubscript{II}
-  phase.
-  \begin{itemize}
-    \item The H\textsubscript{II} phase is an easier to geometry to model
-    and analyze.
-    \item We also have detailed structural data which is necessary for validating
-    our model.
-    \item All of the analysis techniques we use can be equally adapted to
-    the more complicated Q\textsubscript{I} phase geometry.
-  \end{itemize}
+  Although the Q\textsubscript{I} phase shows the most promise for practical 
+  applications, the focus of this work will be on the H\textsubscript{II}
+  phase. The H\textsubscript{II} phase is an easier to geometry to model
+  and analyze. We also have detailed structural data which is necessary for 
+  validating our model. All of the analysis techniques we use can be equally
+  adapted to the more complicated Q\textsubscript{I} phase geometry.
 
   There are few molecular simulation studies which study structure and transport
-  in LLC systems.
-  \begin{itemize}
-    \item Mondal \textit{et al.} used MD simulations to study the self assembly of gemini 
-    surfactants and observed the formation of H\textsubscript{II} and Q\textsubscript{I}
-    phases depending on water content.\cite{mondal_self-assembly_2013}
-    \item Mantha and Yethiraj as well as Roy \textit{et al.} studied the dynamics of confined 
+  in LLC systems. Mondal \textit{et al.} used MD simulations to study the self assembly 
+  of gemini surfactants and observed the formation of H\textsubscript{II} and
+  Q\textsubscript{I} phases depending on water content.~\cite{mondal_self-assembly_2013}
+  Mantha and Yethiraj as well as Roy \textit{et al.} studied the dynamics of confined 
   water in these systems and showed orders of magnitude differences in their motion
   dependent on system geometry.~\cite{mantha_dynamics_2016,roy_water_2016}
-    \item Jackson \textit{et al.} as well as Mantha \textit{et al.} have combined experiment with simulation
-    in order to show how the choice of monomer head group counterion regulate water 
-    dynamics.~\cite{jackson_ion-specific_2018,mantha_counterion-regulated_2018}
-    \item Sakamoto \textit{et al}. and Nada \textit{et al}. observed the dynamics of water molecules
-    and ions and hypothesized transport mechanisms in a simplified model of an LLC
-    nanopore.~\cite{sakamoto_development_2018,nada_transport_2020}
-  \end{itemize}
+  Jackson \textit{et al.} as well as Mantha \textit{et al.} have combined experiment
+  with simulation in order to show how the choice of monomer head group counterion 
+  regulate water dynamics.~\cite{jackson_ion-specific_2018,mantha_counterion-regulated_2018}
+  Sakamoto \textit{et al}. and Nada \textit{et al}. observed the dynamics of water 
+  molecules and ions and hypothesized transport mechanisms in a simplified model of
+  an LLC nanopore.~\cite{sakamoto_development_2018,nada_transport_2020}
 
@@
     \item What is the nanoscopic structure?
-    	\begin{itemize}
-    	  \item Before we can try to understand the molecular mechanisms of solute
+
+    	  Before we can try to understand the molecular mechanisms of solute
     	  transport, we need to ensure that we model the chemical environment
     	  within the nanopores in a way that is consistent with experiment.
-    	  \item We use experimental structural data in order to validate our model.
-    	\end{itemize}
+    	  We use experimental structural data in order to validate our model and
+    	  understand the sensitivity of the model to build parameters.
+
     \item Which solute-membrane interactions have the greatest influence on transport rates?
-    	\begin{itemize}
-    	  \item After gaining a detailed picture of the nanopore structure, we can 
-    	  feel confident that solutes in this system will experience the same 
-    	  interactions which are present in a real system.
-    	  \item We create independent systems for each of 20 small polar solutes 
-    	  and observe transport mechanisms whose dominance is dependent on
-    	  solute chemical functionality.
-    	  \item We characterize three different trapping mechanisms which lead
-    	  to subdiffusive transport behavior.
-    	\end{itemize}
-    %MRS: maybe talk more about the stochastic modeling itself; for example, could phrase it in terms of
-    %how you can test mechanistic models to see if they are consistent with the timeseries, and then how those models
-    %can be further extrapolated to physical observables even if the MD simulations cannot. 
-    %MRS: this MIGHT include using the effective diffusion in a solution/diffusion model.
-    %\item Can we estimate experimentally-relevant macroscopic properties?
-    %BJC2: modified thesis
+
+    	  After gaining a detailed picture of the nanopore structure, we can 
+    	  feel confident that solutes in this system will experience qualitatively 
+    	  similar interactions which are present in a real system. We create independent
+    	  systems for each of 20 small polar solutes and observe transport mechanisms
+    	  whose dominance is dependent on solute chemical functionality. We characterize
+    	  three different trapping mechanisms which lead to subdiffusive transport behavior.
+
     \item Can we formulate mechanistic models whose dynamical properties are consistent with our
     molecular simulations and can be used to extrapolate macroscopic behavior which MD simulations cannot.
-    	\begin{itemize}
-    	  \item Using our qualitative understanding of the dominant trapping mechanisms,
+
+		  Using our qualitative understanding of the dominant trapping mechanisms,
     	  we develop stochastic time series models which we can use to mimic solute dynamic
     	  behavior on time scales orders of magnitude longer than our simulations. 
-    	  \item We attempt to reproduce both quantitative and qualitative solute trajectory
-    	  behavior on MD simulation-length timescales.
-    	  \item We then show how we can use our most promsiing model in order to connect 
-    	  microscopic transport to macroscopic flux and selectivity.
-    	\end{itemize}
+    	  We attempt to reproduce both quantitative and qualitative solute trajectory
+    	  behavior on MD simulation-length timescales. We then show how we can use our 
+    	  most promsiing model in order to connect microscopic transport to macroscopic
+    	  flux and selectivity.
 
     \item How can time series data directly inform us about transport mechanisms?
-    	\begin{itemize}
-    	  \item Although our stochastic models show great promise, their development 
-    	  require some qualitative and quantitative understanding of dominant transport
-    	  mechanisms.
-    	  \item In the final chapter, we use the infinite hidden Markov model in order
-    	  to automatically detect and parameterize a unknown number of hidden dynamical modes
-    	  exhibited by solute time series. 
-    	  \item This more flexible approach allows us to both infer mechanisms based 
-    	  on differences in dynamical behavior and generate stochastic trajectory realizations
-    	  which we can use to predict flux and selectivity. 
-    	\end{itemize}
+
+    	  Although our stochastic models show great promise, their development requires
+    	  some qualitative and quantitative understanding of dominant transport
+    	  mechanisms. In the final chapter, we use the infinite hidden Markov model in
+    	  order to automatically detect and parameterize a unknown number of hidden 
+    	  dynamical modes exhibited by solute time series. This more flexible approach
+    	  allows us to both infer mechanisms based on differences in dynamical behavior
+    	  and generate stochastic trajectory realizations which we can use to predict
+    	  flux and selectivity.
+
   \end{enumerate}
@@
 
-  %BJC2: Should I just put title with reference? Or full citation?
-  \noindent\textit{Chapter 2}: adapted from manuscript entitled ``Understanding the 
-  Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes." 
-  published in the Journal of Physical Chemistry B.~\cite{coscia_understanding_2019} \\
+  %MRS: maybe put supporting information for each chapter at the end of the chapter so it's in one place?
+  %BJC3: it makes the numbering a little confusing. I'll see if there's a way around it.
 
-  \noindent\textit{Chapter 3}: adapted from manuscript entitled ``Chemically Selective 
-  Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane."
-  published in the Journal of Physical Chemistry B.~\cite{coscia_chemically_2019} \\
+%  \noindent\textit{Chapter 2}: adapted from manuscript entitled ``Understanding the 
+%  Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes." 
+%  published in the Journal of Physical Chemistry B.~\cite{coscia_understanding_2019} \\
+%
+%  \noindent\textit{Chapter 3}: adapted from manuscript entitled ``Chemically Selective 
+%  Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane."
+%  published in the Journal of Physical Chemistry B.~\cite{coscia_chemically_2019} \\
+%    
+%  \noindent\textit{Chapter 4}: adapted from a manuscript in review with Physical Review E, entitled 
+%  ``Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+%  with Time Series Modeling". The final manuscript may change based on reviewer feedback. \\
+%    
+%  \noindent\textit{Chapter 5}: adapted from the draft of a manuscript in preparation with the working
+%  title ``Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
+%  of Solute Trajectories in Nanostructured Membranes." The content will change as the
+%  draft is finalized and after reviewer feedback.
+
+  \noindent\textit{Chapter 2}: adapted from Coscia, B. J.; Yelk, J.; Glaser, M. A.; Gin, D. L.; Feng, X.; Shirts,
+  M. R. Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer
+  Membranes. J. Phys. Chem. B 2019, 123, 289-309. \\
+
+  \noindent\textit{Chapter 3}: adapted from Coscia and Shirts. Chemically Selective Transport in a Cross-Linked 
+  H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane. J. Phys. Chem. B 2019, 123, 6314-6330. \\
 
   \noindent\textit{Chapter 4}: adapted from a manuscript in review with Physical Review E, entitled 
-  ``Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+  "Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
   with Time Series Modeling". The final manuscript may change based on reviewer feedback. \\
@@
   \noindent\textit{Chapter 5}: adapted from the draft of a manuscript in preparation with the working
-  title ``Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
+  title "Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
   of Solute Trajectories in Nanostructured Membranes." The content will change as the
   draft is finalized and after reviewer feedback.
-
-%  Chapter 2 is adapted 
-%  \begin{itemize}
-%    %BJC2: Should I just put title with reference? Or full citation?
-%    \item Chapter 2 is adapted from Coscia, B. J.; Yelk, J.; Glaser, M. A.; Gin, D. L.; Feng, X.; Shirts,
-%    M. R. Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer
-%    Membranes. J. Phys. Chem. B 2019, 123, 289-309.
-%    \item Chapter 3 is adapted Coscia and Shirts. Chemically Selective Transport in a Cross-Linked 
-%    H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane. J. Phys. Chem. B 2019, 123, 6314-6330. 
-%    \item Chapter 4 is adapted from a manuscript in review with Physical Review E, entitled 
-%    "Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
-%    with Time Series Modeling". The final manuscript may change based on reviewer feedback.
-%    \item Chapter 5 is adapted from the draft of a manuscript in preparation with the working
-%    title "Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
-%    of Solute Trajectories in Nanostructured Membranes."
-%  \end{itemize}

### 2020-04-03 Ben_Manuscripts/hdphmm/Outline.tex
New script for calculating local density at arbitrary points in unit cell

@@
   \section{Results and Discussion}
-  %MRS2: how stable are the results to realizations of the system
+
   \subsection{Inferring Solute Transport Mechanisms}
 
-  Clustering parameters sets results in X distinct dynamical modes.
+  % BJC: I'll use an example molecule for this section. I'll put files up so
+  % that people can look at any trajectory.
+
+  Solutes in this system show a wide range of behavior influenced by the 
+  heterogeneity of the nanostructure as well as the interactions between 
+  monomers and solute chemical functionality.
+
+  The IHMM does a sufficient job of capturing differences in solute dynamics
+  for individual trajectories.
   \begin{itemize}
-    \item In the figure below, we show time series simulations that qualitatively
-    illustrate the difference in dynamical behavior between modes.
+    \item In Figure TBD, we show the states identified by the IHMM for a single
+    methanol trajectory. The IHMM found x number of states, with y of them 
+    existing for an appreciable amount of time (quantify this).
   \end{itemize}
 
-  %BJC1: a figure showing some representative fluctuations in each mode
-
-  \noindent We can relate the identified states back to transport mechanisms.
+  Depending on the path followed, solute trajectories show diverse behavior.
   \begin{itemize}
-  	\item More detailed discussion of identified states
-  	\item How size of fluctuations, autoregressive parameters are influenced by trapping mechanisms
-  	\item How do these states compare to those identified in our previous work?
-  	\item Any new states?
+    \item Some show lots of movement
+    \item Some show almost no movement
+    \item While all trajectories might not be the same, it is likely that 
+    multiple trajectories might share some similar behavior.
   \end{itemize}
 
+  Appropriate clustering helps up group these similarities so that we can 
+  more easily interpret the MD trajectories.
+
+  Although we want to narrow the sets of VAR parameters, it is
+  important not to prune too much.
+  \begin{itemize}
+    \item Since we are working with VAR parameters in two dimensions, there
+    is a potential for many distinct combinations of behavior.
+    \item If we only consider the diagonal entries of the $A$ and $\Sigma$ matrices,
+    a total of four independent variables, we can consider clustering each 
+    into at least two groups (higher versus lower values), which implies $2^4$ distinct
+    dynamical behaviors. 
+    %BJC: this might belong in methods
+    %BJC: need to come up with a good justification for choice of distance threshold.
+    \item If we set the distance threshold too high, visually non-similar states 
+    will be clustered together.
+    \item If we set the distance threshold too low, we will identify more states 
+    than are needed to sufficiently describe the system.
+    \item Maybe a plot showing what the trajectories look like with too much clustering. 
+  \end{itemize}
+
+  In order to not negelect the large variety of behavior present in this system, we
+  aim to strike a balance between clustering and faithfully representing all of
+  the types of behavior observed.
+
+  % BJC: Show a trajectory that shares many states with another state. Color them the same to show that clustering did something
+
+  As should be expected, it would be unlikely to expect only a handful of states.
+  However, we are well versed in the types of interactions that exist in this system:
+  \begin{itemize}
+    \item Hydrogen bonding
+    \item Sodium Ion association
+    \item Distance from pore center
+    \item Heterogeneous density
+    \item By simultaeneously viewing these metrics alongside state predictions, we 
+    can form a picture of how solute's behave in these systems.
+    \item And we can determine which of them contribute the most to MSD (?)
+  \end{itemize}
+
+  A plot of the different states found and talk about how they are different
+
+  Here are the major observations based on this trajectory.
+
+  Say how this approach is useful and may be best applied carefully on a case by 
+  case basis in order to maximize undrestanding. But this is much simpler than
+  studying the MD trajectories.
+
   \subsection{Reproducing MD Trajectories and MSDs with the IHMM}
+  % BJC: don't forget to mention in the methods that clustering is necessary in order to
+  % construct a single set of parameters used to project MSDs
 
   \noindent Trajectory realizations qualitatively match MD simulation trajectories.
+
+  More distinct states generally leads to better qualitative matches.
 

### 2020-04-04 Ben_Manuscripts/hdphmm/Outline.tex
New figures and updates to outline

--- 2020-04-02 Ben_Manuscripts/hdphmm/Outline.tex
@@
     \item Parameter estimation is iterative. Therefore, we looked for convergence 
-    of each entry in the $c$ vector as well as the $A$ and $\Sigma$ matrices of 
+    of each entry in the $\mathbf{c}$ vector as well as the $A$ and $\Sigma$ matrices of 
     Equation~\ref{eqn:var}.
@@
     $x$ and $y$ (see Figure~\ref{fig:cartesian_cylinder}).
-    %MRS3: I'm not following the below? I don't know that we WANT to find more states, in my mind doing it this way 
-    %the math is simpler this way since we don't have to rewrite things in term of radial diffusion
-    %MRS3: we can brainstorm this as needed!
-    \item By using 2 dimensions, rather than a single radial dimension, we
-    increase the likelihood of finding more states since a single radial
-    mean can be represented by an infinite number of $x$ and $y$ coordinate combinations.
+    \item By working in cartesian coordinates, we avoid mathematical complexity
+    introduced by cylindrical coordinates while estimating the state sequence.
   \end{itemize}
@@
     parameterize the prior on $\mathbf{c}$ in an intelligent way.
-    \item The prior parameters should be chosen such that the means of 
-    each state lie within a region of reasonable probability of the prior (see
+    \item The prior parameters should be chosen such that the mean level of 
+    each state lies within a region of reasonable probability of the prior (see
     Figure~\ref{fig:prior_guesses}).
@@
 
-  % BJC2: It's probably possible to convert to from x, y, z to r, z but
-  % I need to figure out the transformation of A. This approach works though.
   We reparameterized the time series, preserving the state sequence, in terms
@@
   meaningful alone due to the system's radial symmetry.
-  % the mean in $r$ is a useful clustering variable.
   \begin{itemize}
-    \item It will also be clearer to analyze the final parameter set in
-    terms of $r$ rather than $x$ and $y$.
     \item We converted the $x$ and $y$ center-of-mass coordinates to $r$.
-%    \item In order to keep the same states found when we applied the algorithm
-%    in 3D, we reapplied the IHMM to the cylindrical trajectories with a fixed 
-%    state sequence, only allowing inference on the VAR(1) parameters.
-    %MRS3: would it be clearer to say you appplied only the inference part of the process on the clustered data?
-    %BJC3: like this?
     \item We fixed the state sequence from the 3D parmeterization and applied the
@@
   \begin{itemize}
-  \item For each solute studied, we identified 200-300 independent states, each
-  with separate VAR(1) parameters. % BJC2: just a guess for now
+  	\item For each solute studied, we identified 200-325 independent states, each
+   	with separate VAR(1) parameters.
    	\item Many of these states exhibit very similar dynamical behavior except their
@@
    	get trapped along a broad and continuous range of $z$ coordinates. 
-   \item Since we do not know the number of states with shared dynamical behavior
-   beforehand, we used a non-parametric Bayesian Gaussian mixture model in order
-   to cluster them. % cite scikit-learn  
-%   \item This is necessary for us to perform any kind of mechanistic speculation.
+  \end{itemize}
+
+  We reduced the parameter space used agglomerative clustering, a hierarchical
+  clustering approach which uses a linkage criteria in order to successively merge
+  similar clusters until a desired intracluster distance threshold or number of
+  clusters is reached. 
+  \begin{itemize}
+   	\item We used the Ward linkage criteria, which works to minimize the sum of
+   	the squared differences within all clusters.
+   	\item We elected to choose the number of clusters rather than the distance
+   	threshold.
+   	\item For our data, non-parameteric methods such as Bayesian Gaussian mixture
+   	models tend to delocalize the clusters in parameter space (see Supporting
+   	Information).
+   	%BJC: will show Gaussian mixture model which has a cluster engulfing another cluster, so it's tails are on both sides of the center cluster.
   \end{itemize}
@@
   % this is the one I'm going with for now.
-  We clustered based on 5 variables: the radial means of each state, the two
-  eigenvalues of $A$ and the two eigenvalues of $\Sigma$.
+  We clustered based on the two diagonal entries of $A$ and the two diagonal entries 
+  of $\Sigma$.
   \begin{itemize}
-   \item Unfortunately, the number of independent parameter sets is too low for
-   clustering in higher dimensions. 
-   \item Ideally, we could use all of the entries of $A$ and $\Sigma$ in addition to 
-   the radial means.
-   \item It would not be helpful to use the means in the $z$ direction because solutes
-   are essentially unbound in that direction.
-   \item However, in our previous work, we observed radially dependent dynamical 
-   behavior.~\cite{coscia_chemically_2019}  % cite new paper eventually too.
+   \item One can choose alternative clustering features, such as the eigenvalues of
+   the $A$ and $\Sigma$ matrices, but we chose their diagonals because they can be
+   easily translated to solute behavior.
+   \item We also chose to cluster the diagonals of each matrix independently before
+   combining the clusters to assign final state labels. 
+   \item If we divide the total states into $m$ clusters based on the diagonal entries
+   of $A$ and, separately, $n$ clusters based on the diagonal entries of $\Sigma$,
+   then there are a total of $mn$ possible cluster combinations.
+   \item This allows slightly more flexibility in the total number of states compared
+   to clustering on all four features at once, since there can be up to, but not 
+   necessarily exactly, $mn$ states. 
+  \end{itemize}
+
+  Choosing the number of clusters can be somewhat subjective so
+  we attempted to add some structure to the selection process by following
+  a set of qualitative and quantitative guidelines.
+  \begin{itemize}
+  	%BJC3: not sure if the commented point worth making.
+%    \item We should expect a relatively high number of states. If we only consider
+%    the diagonal entries of the $A$ and $\Sigma$ matrices, a total of four independent
+%    variables, we can consider clustering each into at least two groups (higher versus
+%    lower values), which implies $2^4$ distinct dynamical behaviors. 
+    \item We used the Silhouette test in order to score the quality of
+    clusters as a function of the number of clusters chosen.
+    \item For our data, the Silhouette test generally favors the lowest number
+    of clusters possible (see Supporting Information).
+    \item However, choosing too few clusters tends to result in 
+    inadequate distinguishment between visually obvious differences in 
+    dynamic behavior.
+    \item This results in finalized parameter sets that are averages of
+    distinct behavior which presents further problems with the predictive
+    modeling that we discuss later on.
+    \item We aimed to maintain the highest Silhouette score, and thus lowest
+    number of clusters, possible while verifying that visually distinct 
+    states stayed separated.
+    \item Based on these guidelines, we decided to group the $A$ and $\Sigma$
+    parameters into five clusters each. 
+	\item Of the 25 distinct states allowed by this formulation, the solutes
+	in this study clustered into 13--18 distinct clusters.
   \end{itemize}
@@
 
-  %MRS3: ``used the IHMM algorithm'' -> ``used the parameter inference part of the IHMM algorithm''?
   We used the parameter inference component of the IHMM algorithm in order to 
@@
   \section{Results and Discussion}
-  %MRS2: how stable are the results to realizations of the system
-  \subsection{Inferring Solute Transport Mechanisms}
 
-  Clustering parameters sets results in X distinct dynamical modes.
+  Solutes in this system show a wide range of behavior influenced by the 
+  heterogeneity of the membrane's nanostructure as well as the interactions 
+  between monomer and solute chemical functionality. 
   \begin{itemize}  
-    \item In the figure below, we show time series simulations that qualitatively
-    illustrate the difference in dynamical behavior between modes.
+  	\item Our application of the IHMM does a good job of identifying and
+  	distinguishing these behaviors.   	
+  	\item Clustering the behaviors helps us to tell a coherent story which
+  	emphasizes those interactions which most heavily influence solute transport.
+  	\item This analysis approach helps us to break down the very complex behavior
+  	exhibited by solutes over long MD trajectories into discrete categories.
   \end{itemize}
 
-  %BJC1: a figure showing some representative fluctuations in each mode
+  \subsection{Automatic Detection of Distinct Dynamical Modes}\label{section:find_modes}
 
-  \noindent We can relate the identified states back to transport mechanisms.
+  %BJC3: I'm not sure if it's worth talking about all of the solutes in this section.
+  % there is a lot to talk about just with methanol (which is all I've done for now -- wanted to
+  % get feedback on analysis approach).
+  %BJC3: I see this more as a demonstration of the model. I think this work has higher
+  % impact potential so I don't want it to be 15 pages.
+  %BJC3: Although, it might be a good idea to include Urea or Acetic acid as a second example
+  % molecule because their behavior is pretty different since their carbonyl group tend to 
+  % associate with sodium a lot.
+
+  %BJC3: obviously can use a better thesis.
+  We showcase this modeling approach by example. 
   \begin{itemize}
-  	\item More detailed discussion of identified states
-  	\item How size of fluctuations, autoregressive parameters are influenced by trapping mechanisms
-  	\item How do these states compare to those identified in our previous work?
-  	\item Any new states?
+    \item In Figure~\ref{fig:mechanism_map}, we plot a representative 2D methanol 
+    trajectory in cylindrical coordinates.
+    \item The coordinates are colored according to the cluster with which methanol's
+    dynamics are most consistent, which implies that this particular methanol 
+    trajctory exhibits 6 distinct dynamical behaviors. 
+    \item The solute timeseries are coupled with color coded bars which describe the
+    solute's local environment and physical interactions that it undergoes at that
+    time frame.
+    \item From the top, they describe whether the solute is associated with sodium,
+    whether the solute is hydrogen bonding with the monomer as well as what part of
+    the monomer it is hydrogen bonding to, the local number density surrounding the
+    solute and the radial location of the solute with respect to the nearest pore
+    center (this information is redundant but can be a useful visual aid). %BJC3: still debating removing that bar
   \end{itemize}
+
+  %BJC3: I still need labels for this plot
+  \begin{figure}
+  \includegraphics[width=\textwidth]{mechanism_map.pdf}
+  \caption{}\label{fig:mechanism_map}
+  \end{figure}
+
+  One can gain significant chemical intuition just by studying plots like
+  Figure~\ref{fig:mechanism_map}.
+  \begin{itemize}
+    \item It is clear that, for methanol, association with sodium is a much rarer
+    interaction than hydrogen bonding with the LLC monomers.
+    \item Methanol hydrogen bonds to all regions of the monomers dependent on
+    its radial position.
+    \item Its fluctuations tend to be smallest when hydrogen bonded or in areas
+    of high local number density. 
+    \item For example, from approximately 75 to 525 ns, methanol appears to be trapped
+    in a high density region of the tails.
+    \item In the time that follows, it enters a region of relatively low density
+    where fluctuations are quite large. 
+    \item During this time period, there is intermittent, short-lived hydrogen 
+    bonding with the oxygen atoms at the tail ends, as suggested by the frequent 
+    state changes during that time period and red slivers in the bar above.
+  \end{itemize}
+
+  %BJC3: I think I'll just skip to the clustered results. I'd like to keep this
+  % paper on the shorter side.
+%  The IHMM does a sufficient job of capturing differences in solute dynamics
+%  for individual trajectories.
+%  \begin{itemize}
+%    \item In Figure TBD, we show the states identified by the IHMM for a single
+%    methanol trajectory. The IHMM found x number of states.
+%  \end{itemize}
+
+%  Depending on the path followed, solute trajectories show diverse behavior.
+%  \begin{itemize}
+%    \item Some show lots of movement
+%    \item Some show almost no movement
+%    \item While all trajectories might not be the same, it is likely that 
+%    multiple trajectories might share some similar behavior.
+%  \end{itemize}
+
+  We may learn the most by studying the dynamical modes common to the majority of 
+  the solute trajectories.
+  \begin{itemize}
+    \item Using the IHMM, we identified 13 total dynamical modes exhibited by 
+    methanol. 
+    \item Of those, 4 appear in at least 50 \% of the methanol trajectories, and
+    2 of them appear in over 90 \% of the methanol trajectories.
+    \item In Figure~\ref{fig:common_states_MET_lines}, we plot representative dynamics
+    of each of the 4 prevelant states.
+    \item Based on their self-transition probabilities, we estimated the average 
+    time spent by each solute in each state (Figure~\ref{fig:dwell_times_MET}).
+    \item States 2 and 4 have long dwell times relative to states 1 and 3 because
+    they have high self-transition probabilities.
+    \item States 1 and 3 show large fluctuations relative to the other states owing
+    to larger covariances in both the axial and radial dimensions. (Figure~\ref{fig:A_sigma_scatter_MET})
+    \item States 1 and 2 have lower autoregressive coefficients relative to states
+    3 and 4.
+    \item All of these states are present in Figure~\ref{fig:mechanism_map} and colored
+    accordingly.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.6\textwidth}
+  \includegraphics[width=\textwidth]{common_states_MET.pdf}
+  \caption{}\label{fig:common_states_MET_lines}
+  \end{subfigure}
+  \begin{subfigure}{0.35\textwidth}
+  \includegraphics[width=\textwidth]{dwell_times_MET.pdf}
+  \caption{}\label{fig:dwell_times_MET}
+  \includegraphics[width=\textwidth]{A_sigma_scatter_MET.pdf}
+  \caption{}\label{fig:A_sigma_scatter_MET}
+  \end{subfigure}
+  \caption{}\label{fig:common_states_MET}
+  \end{figure}
+
+  %BJC3: I'm struggling a bit with this part of the analysis. The story isn't as clear
+  % cut as I want because it seems like states which contribute to the same cluster behave
+  % the way they do for somewhat varied reasons. Hence the short paragraph after this one.
+  We can attempt to understand the behavior described in Figure~\ref{fig:common_states_MET}
+  further by relating them to their interactions with the membrane. 
+  \begin{itemize}
+    \item It is clear that solutes can behave similar in different regions of the 
+    membrane because each state hydrogen bonds with LLC atoms located from the monomer head
+    groups to the tails. 
+    %BJC3: The following is a hypothesis to be tested.
+    \item The key difference is the lifetime of these interactions. 
+    \item When in a trapped state (one with smaller covariance like 2 and 4), hydrogen bond
+    lifetimes are generally longer.
+    \item While hydrogen bonds occur in states 1 and 3, the lifetimes are shorter, perhaps
+    broken by fluctuations in their local environment.
+  \end{itemize}
+
+  It is important to understand that the clustered parameter sets are
+  essentially summaries of many related behaviors. Therefore, the most thorough
+  understanding of a specific segment will be gained using descriptive visualizations
+  like Figure~\ref{fig:mechanism_map}. But this model very clearly tells the user where
+  to look.
+  %BJC3: could do a case study of sorts on a chosen segment
+
+  %BJC3: this figure is not even close to done
+  %BJC3: I've tried a couple different things to look at the hbonds. The other was 
+  % how often they are hydrogen bonded in general versus not hydrogen bond. They all
+  % hydrogen bond about the same amount. So I think hbond lifetimes may be the key. 
+  % I need to implement this first to test that hypothesis.
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{hbond_pi_charts.pdf}
+  \caption{}\label{fig:hbond_pichart}
+  \end{figure}
 
@@
 
-  \noindent Trajectory realizations qualitatively match MD simulation trajectories.
-
+  We can use the IHMM in order to generate stochastic trajectory realizations
+  which bear qualitatively similar characteristics to those output
+  by our MD simulations.
   \begin{itemize}
-    %MRS2: think about how to quantify the simiilarity of the hopping and trapping behavior.
-    \item Look for hopping and trapping behavior
+    \item Because we clustered the data, we are left with a single transition
+    probability matrix which allows transitions between dynamical behaviors
+    shared by the 24 MD trajectories.
+    \item Therefore, the realizations generated by our model are representative
+    of the average behavior of solutes studied.
+    \item In Figure~\ref{fig:trajectory_realizations_MET}, we show some stochastic
+    realizations generated by our models compared directly to MD.
+    \item The trajectories show clear periods of entrapment with intermittent hops.
   \end{itemize}
 
-  \noindent MSDs generated from stochastic trajectories match those from MD.
+  % BJC3: It might be good to show a few MD trajectories since they vary somewhat widely
+  % in behavior.
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{trajectory_realizations_MET.pdf}
+  \caption{}\label{fig:trajectory_realizations_MET}
+  \end{figure}
+
+  \noindent The MSDs calculated by stochastic realizations of our model are
+  quantitatively similar to MD.
   \begin{itemize}
-    %MRS2: again, think about the best ways to quantify similar between MD and stochastic trajectories.
-  	\item Look at curvature and 1-$\sigma$ confidence intervals
+  	\item For all solutes except acetic acid, our predicted MSD curve lie close to
+  	but below the 1$\sigma$ confidence intervals of MD.
+  	\item However, in these cases, the average MD MSDs are driven up by single trajectories
+    with uncharacteristically large MSDs.
+    \item If we remove these uncharacteristic trajectories, the agreement between 
+    MD and our realizations improves. 
+    % BJC3: I'm not sure the best course of action. I've double checked the bootstrapping
+    % procedure and it make sense to me.
+    % BJC3: I could show how it's possible to get good agreeement with MD by only
+    % generating 24 solute trajectories since in some cases, outliers heavily weight the averages.
+    \item Acetic acid has no obvious outliers and shows good agreement between MD and
+    IHMM realizations.
   \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msd_MET.pdf}
+  \caption{}\label{fig:msd_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msd_GCL.pdf}
+  \caption{}\label{fig:msd_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msd_URE.pdf}
+  \caption{}\label{fig:msd_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{msd_ACH.pdf}
+  \caption{}\label{fig:msd_ACH}
+  \end{subfigure}
+  \end{figure}
+
+  % BJC3: maybe need to talk about the curvature. Our model shouldn't have noticeable
+  % curvature because it's only correlated with one step
 
@@
 
-  \noindent We can predict macroscopic flux and selectivity.
+  %BJC3: I still need to implement this into my mean first passage time code, but it will very closely follow the 
+  % methodology of the last paper. However, if I see that the decay in flux is
+  % near 2 (which I expect), then I may add a short section showing how you can
+  % simply use the ratio of the MSD slopes in order to estimate selectivity.
+  % I think they should give the same results. Haven't tested it yet though.
+
+  We can use realizations of our model in order to predict macropscopic flux and
+  selectivity.
   \begin{itemize}
-  	\item Flux as function of pore length
-  	\item Selectivity as function of pore length (if flux scaling is length-dependent)
+    \item For various length pores, we constructed distributions of first passage times for each solute and
+    fit them to Equation~\ref{eqn:passage_times} in order estimate the mean 
+    first passage time (MFPT). 
+    \item We plotted the inverse of MFPT, the solute flux, versus pore length
+    in Figure TBD.
+    \item Flux rapdily decays with pore length.
+    \item Selectivity is simply the ratio of the fluxes for this system.
+  \end{itemize}
+
+  %BJC3: this paragraph is speculative.
+  We can use the slopes of the MSD curves to estimate selectivity in a simpler way.
+  \begin{itemize}
+  	\item As in our previous work, we fit the flux curves to a decaying power law function
+  	of the form:
+  	\begin{equation}
+    	Ae^{-\beta}
+  	\end{equation}
+  	\item We find that in all cases, $\beta$ is equal to 2. This is consistent with Brownian
+	motion which implies long term linear behavior of the MSD curves. 
+	\item Since the diffusion constant is linearly proportional to the slope of the MSD, and 
+	selectivity in this system can be estimated as the ratio of diffusion constants, we can 
+	estimate selectivity directly based on the slopes of our stochastically simulated MSD curves.
   \end{itemize}
@@
 
+  \noindent We showcase this modeling approach by example, but it is important to
+  recognize the generality of this analysis.
+
   \noindent We can use the IHMM to help identify mechanisms by relating the latent
@@
 
-  \noindent We can use the IHMM to predict macroscopic transport properties. \\
-
-  %MRS2: below probably doesn't need to be stated?
-  \noindent The IHMM is not limited to the H\textsubscript{II} phase.
+  \noindent We show how one can use the IHMM to predict macroscopic transport properties. \\
 

### 2020-04-05 Ben_Manuscripts/hdphmm/Outline.tex
First pass of comments.

@@
     %BJC3: tried to make more clear
+    %MRS4: physically mention what the base distribution is?
    \item The concentration parameter, $\gamma$, expresses one's confidence in the 
@@
     % Maybe I should reach out to emily fox to see how she would prefer I cite the software?
+    %MRS4: yes, she how she wants to cite it.
     %MRS3: be a bit more specific about what the criteria were for convergence.
     %BJC3: See if that's better
+    %MRS4: But what quantitative criteria did you use to determine convergence?
     \item Parameter estimation is iterative. Therefore, we looked for convergence 
@@
     \item We refer the interested reader to much more extensive descriptions of 
-    %MRS3: be more specific about which parts from the above are in the references
-    %BJC3: made more specific
     the inference and sampling procedures used to estimate the VAR(1) parameters
@@
   \includegraphics[width=\textwidth]{prior_guesses.pdf}
+  %MRS4: remind people what $c$ physically represents here. 
   \caption{The parameters of the prior on $c$ (black line) should be chosen such
@@
   \begin{itemize}
+    %MRS4: Do you need to convert the covariance to cylintrical coordinates here before clustereing? 
     \item We converted the $x$ and $y$ center-of-mass coordinates to $r$.
@@
    	get trapped along a broad and continuous range of $z$ coordinates. 
+  %MRS4: Maybe better to phrase above in terms of the symmetry in z. Why does it matter the range is continuous?
   \end{itemize}
@@
    easily translated to solute behavior.
+   %MRS4: suggest translating them here into solute behavior for the reader!
    \item We also chose to cluster the diagonals of each matrix independently before
@@
    necessarily exactly, $mn$ states. 
+   %MRS4: so no clustering based on transition probablity, correct?
   \end{itemize}
@@
    trajectories.
-   %MRS3: seems like you should just be able to lump together the IHMM states to generate the IHMM estimate of T?
-   %BJC3: That's what I do. Maybe I'm misunderstanding your suggestion. I added a little bit to the sentence
-   % above to try and make more clear.
   \end{itemize}
@@
   %BJC: can make this discussion somewhat short since it's already in previous paper. 
+  %MRS4: yes, can be short
   % Should probably just hit all the main equations quickly.
@@
   % molecule because their behavior is pretty different since their carbonyl group tend to 
+  %MRS4: there should be SOME summary information on the other molecules, but it can just be the conclusions.
   % associate with sodium a lot.
@@
     time frame.
+    %MRS: maybe number (1-4) or label (a-d) the rows as well. 
     \item From the top, they describe whether the solute is associated with sodium,

### 2020-04-05 Ben_Manuscripts/thesis/structure.tex
Updates to outline and minor changes to figures

@@
 
-  More highly selective nanoporous membranes would be extremely useful for
-  performing complex aqueous separations with seawater and various types of
-  wastewater. For example, Sodium chloride and boron in seawater
-  \cite{fritzmann_state---art_2007} and organic micropollutants found in
-  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
-  represent just a few of the diverse contaminants of water sources. By
-  efficiently separating contaminants from feed solutions with highly selective
-  membranes, it is possible to reduce the number of required membrane passes and
-  post-treatment steps needed for a given filtration process
-  \cite{werber_materials_2016}, thus lowering energy requirements. Additionally,
-  one can also extract valuable resources from the feed streams. For example,
-  flowback water produced during hydraulic fracturing of shale formations
-  contains dissolved species such as acetate whose extraction has economic value
-  \cite{dischinger_application_2017}.
-
-  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
-  filtration processes that can be used to separate solutes on the order of 1 nm
-  in size and smaller, including ions. However, commercially available amorphous
-  RO membranes and porous NF membranes lack uniformity, which severely impacts
-  their selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
-  fabrication involves the spontaneous assembly of polymers into disordered
-  structures that offer separation pathways that are tortuous and polydisperse in
-  size \cite{werber_materials_2016}. Tortuosity increases the effective length
-  that a solute must travel, while pore size polydispersity limits membrane
-  selectivity.
-
-  Ordered, nanostructured porous membrane materials have become an increasingly popular
-  research area for aqueous separation applications because they offer the
-  ability to control pore architecture at the molecular scale, thereby
-  permitting the design of solute-specific separation membranes
-  \cite{humplik_nanostructured_2011}. However, their development has been limited
-  by the ability to synthesize and scale various technologies. Graphene sheets
-  are atomically thick, which results in excellent water permeability but defects
-  during manufacturing severely impact selectivity
-  \cite{cohen-tanugi_multilayer_2016}.  Molecular dynamics (MD) simulations of
-  carbon nanotubes have shown promise \cite{humplik_nanostructured_2011}, but
-  synthetic techniques are unable to achieve scalable alignment and pore
-  monodispersity \cite{hata_water-assisted_2004,maruyama_growth_2005}.
-  Consequently, there is a need for new materials that could provide scalable
-  nanostructured porous membranes.
-
-  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
-  (LLC) membranes can be produced at moderate scale and may be capable of
-  performing highly selective separations. LLCs are amphiphilic molecules that
-  have the ability to self-assemble into porous nanostructures
-  \cite{smith_ordered_1997} and can be cross-linked to create mechanically strong
-  membrane films with periodic pores on the order of 1 nm in diameter
-  \cite{zhou_supported_2005}. Unlike the pores in most commercial NF membranes,
-  polymeric LLC membrane pores are uniform in size because they are formed by
-  self-assembly. Since LLC polymer membranes lack an appreciable pore size
-  distribution, they inherently exhibit high selectivity due to their strict
-  molecular weight cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the
-  LLC monomers examined in this paper are salts, and therefore lead to Donnan
-  exclusion of ions in solution. The membrane gains a net surface charge when
-  counterions from the head groups that line the pore walls escape into the feed
-  solution in an effort to balance the gradients of concentration and electric
-  potential \cite{donnan_theory_1995}.
-
-  The feasibility of nanostructured LLC polymer membranes for selective
-  separations has been demonstrated using LLC monomers that form the type 1
-  bicontinuous cubic (Q\textsubscript{I})
-  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
-  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
-  phases. When separating organic solutes from NaCl, Q\textsubscript{I}-phase
-  membrane filtration experiments have shown selectivity 2--3 times higher than
-  commercial RO and 6--12 times higher than commercial NF membranes
-  \cite{dischinger_application_2017}. When separating a series of various sized
-  dyes, the H\textsubscript{II}-phase membrane showed complete rejection of dyes
-  bigger than 1.2 nm in size \cite{zhou_supported_2005}.
-
-  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:hex_packing_simple}) has a
-  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
-  The H\textsubscript{II} phase forms at room temperature in the presence of
-  ca.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
-  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
-  form the same hexagonal columnar structure which, in the literature, has been
-  referred to as the Col\textsubscript{h} thermotropic
-  phase\cite{feng_scalable_2014}. Q\textsubscript{I}-phase membranes consist of
-  a tortuous network of three dimensionally interconnected pores that prevent
-  optimal through-plane transport. In contrast, the densely packed, non-tortuous
-  and uniform sized pores of H\textsubscript{II}-phase membranes represent the
-  ideal geometry for achieving high solute
-  flux\cite{matyka_tortuosity-porosity_2008}. However, the hexagonally packed LC
-  domains of the H\textsubscript{II}-phase generally form mutually unaligned
-  domains, which hurts membrane permeability. This domain scale misalignment had
-  inhibited further development of this technology, and research efforts were
-  focused on the Q\textsubscript{I} phase, whose geometry does not require
-  alignment~\cite{zhou_new_2007}.
-
-  However, recently researchers have learned how to macroscopically align the
-  hexagonal domains which has revived research into H\textsubscript{II}-phase LLC
-  polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
-  domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
-  with subsequent cross-linking to lock the structure in
-  place\cite{feng_scalable_2014}. In 2016, Feng et al.~showed that one could
-  also obtain the same result by confining the neat monomer between PDMS or glass
-  substrates since hexagonal mesophases preferentially anchor perpendicular to
-  both surfaces\cite{feng_thin_2016}. Current experimental efforts are focused
-  on extending the method to the H\textsubscript{II} phase and characterizing
-  the performance of these newly aligned systems.
-
-  \begin{figure}
-	\centering
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{NaGA3C11.pdf}
-		\caption{}~\label{fig:monomer}
-	\end{subfigure}
-	\begin{subfigure}{.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
-		\caption{}~\label{fig:atomistic_monomer}
-	\end{subfigure}
-	\begin{subfigure}{0.3\linewidth}
-		\centering
-		\includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
-		\caption{}~\label{fig:wedge}
-	\end{subfigure}
-		\begin{subfigure}{0.4\linewidth}
-		\centering
-		\includegraphics[width=0.6\textwidth]{columns.pdf}
-		\caption{}~\label{fig:wedge_layer}
-	\end{subfigure}
-	\begin{subfigure}{0.4\linewidth}
-		\centering
-		\includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
-		\caption{}~\label{fig:hex_packing_simple}
-	\end{subfigure}
-	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
-	exhibits wedge-like character. (d) Monomers stack on top of each other to
-	create columns with short range order, then assemble into pores with 
-	hydrophilic head groups (blue) facing towards the pore center. (e) The 
-	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
-  \end{figure}
+%  More highly selective nanoporous membranes would be extremely useful for
+%  performing complex aqueous separations with seawater and various types of
+%  wastewater. For example, Sodium chloride and boron in seawater
+%  \cite{fritzmann_state---art_2007} and organic micropollutants found in
+%  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
+%  represent just a few of the diverse contaminants of water sources. By
+%  efficiently separating contaminants from feed solutions with highly selective
+%  membranes, it is possible to reduce the number of required membrane passes and
+%  post-treatment steps needed for a given filtration process
+%  \cite{werber_materials_2016}, thus lowering energy requirements. Additionally,
+%  one can also extract valuable resources from the feed streams. For example,
+%  flowback water produced during hydraulic fracturing of shale formations
+%  contains dissolved species such as acetate whose extraction has economic value
+%  \cite{dischinger_application_2017}.  
+%
+%  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
+%  filtration processes that can be used to separate solutes on the order of 1 nm
+%  in size and smaller, including ions. However, commercially available amorphous
+%  RO membranes and porous NF membranes lack uniformity, which severely impacts
+%  their selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
+%  fabrication involves the spontaneous assembly of polymers into disordered
+%  structures that offer separation pathways that are tortuous and polydisperse in
+%  size \cite{werber_materials_2016}. Tortuosity increases the effective length
+%  that a solute must travel, while pore size polydispersity limits membrane
+%  selectivity.
+%
+%  Ordered, nanostructured porous membrane materials have become an increasingly popular
+%  research area for aqueous separation applications because they offer the
+%  ability to control pore architecture at the molecular scale, thereby
+%  permitting the design of solute-specific separation membranes
+%  \cite{humplik_nanostructured_2011}. However, their development has been limited
+%  by the ability to synthesize and scale various technologies. Graphene sheets
+%  are atomically thick, which results in excellent water permeability but defects
+%  during manufacturing severely impact selectivity
+%  \cite{cohen-tanugi_multilayer_2016}.  Molecular dynamics (MD) simulations of
+%  carbon nanotubes have shown promise \cite{humplik_nanostructured_2011}, but
+%  synthetic techniques are unable to achieve scalable alignment and pore
+%  monodispersity \cite{hata_water-assisted_2004,maruyama_growth_2005}.
+%  Consequently, there is a need for new materials that could provide scalable
+%  nanostructured porous membranes. 
+%
+%  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
+%  (LLC) membranes can be produced at moderate scale and may be capable of
+%  performing highly selective separations. LLCs are amphiphilic molecules that
+%  have the ability to self-assemble into porous nanostructures
+%  \cite{smith_ordered_1997} and can be cross-linked to create mechanically strong
+%  membrane films with periodic pores on the order of 1 nm in diameter
+%  \cite{zhou_supported_2005}. Unlike the pores in most commercial NF membranes,
+%  polymeric LLC membrane pores are uniform in size because they are formed by
+%  self-assembly. Since LLC polymer membranes lack an appreciable pore size
+%  distribution, they inherently exhibit high selectivity due to their strict
+%  molecular weight cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the
+%  LLC monomers examined in this paper are salts, and therefore lead to Donnan
+%  exclusion of ions in solution. The membrane gains a net surface charge when
+%  counterions from the head groups that line the pore walls escape into the feed
+%  solution in an effort to balance the gradients of concentration and electric
+%  potential \cite{donnan_theory_1995}.    
+%
+%  The feasibility of nanostructured LLC polymer membranes for selective
+%  separations has been demonstrated using LLC monomers that form the type 1
+%  bicontinuous cubic (Q\textsubscript{I})
+%  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
+%  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
+%  phases. When separating organic solutes from NaCl, Q\textsubscript{I}-phase
+%  membrane filtration experiments have shown selectivity 2--3 times higher than
+%  commercial RO and 6--12 times higher than commercial NF membranes
+%  \cite{dischinger_application_2017}. When separating a series of various sized
+%  dyes, the H\textsubscript{II}-phase membrane showed complete rejection of dyes
+%  bigger than 1.2 nm in size \cite{zhou_supported_2005}. 
+%
+%  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:hex_packing_simple}) has a
+%  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
+%  The H\textsubscript{II} phase forms at room temperature in the presence of
+%  ca.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
+%  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
+%  form the same hexagonal columnar structure which, in the literature, has been
+%  referred to as the Col\textsubscript{h} thermotropic
+%  phase\cite{feng_scalable_2014}. Q\textsubscript{I}-phase membranes consist of
+%  a tortuous network of three dimensionally interconnected pores that prevent
+%  optimal through-plane transport. In contrast, the densely packed, non-tortuous
+%  and uniform sized pores of H\textsubscript{II}-phase membranes represent the
+%  ideal geometry for achieving high solute
+%  flux\cite{matyka_tortuosity-porosity_2008}. However, the hexagonally packed LC
+%  domains of the H\textsubscript{II}-phase generally form mutually unaligned
+%  domains, which hurts membrane permeability. This domain scale misalignment had
+%  inhibited further development of this technology, and research efforts were
+%  focused on the Q\textsubscript{I} phase, whose geometry does not require
+%  alignment~\cite{zhou_new_2007}. 
+%
+%  However, recently researchers have learned how to macroscopically align the
+%  hexagonal domains which has revived research into H\textsubscript{II}-phase LLC
+%  polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
+%  domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
+%  with subsequent cross-linking to lock the structure in
+%  place\cite{feng_scalable_2014}. In 2016, Feng et al.~showed that one could
+%  also obtain the same result by confining the neat monomer between PDMS or glass
+%  substrates since hexagonal mesophases preferentially anchor perpendicular to
+%  both surfaces\cite{feng_thin_2016}. Current experimental efforts are focused
+%  on extending the method to the H\textsubscript{II} phase and characterizing
+%  the performance of these newly aligned systems.
+%
+%  \begin{figure}
+%	\centering
+%	\begin{subfigure}{.3\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{NaGA3C11.pdf}
+%		\caption{}~\label{fig:monomer}
+%	\end{subfigure}
+%	\begin{subfigure}{.3\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
+%		\caption{}~\label{fig:atomistic_monomer}
+%	\end{subfigure}
+%	\begin{subfigure}{0.3\linewidth}
+%		\centering
+%		\includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
+%		\caption{}~\label{fig:wedge}
+%	\end{subfigure}
+%		\begin{subfigure}{0.4\linewidth}
+%		\centering
+%		\includegraphics[width=0.6\textwidth]{columns.pdf}
+%		\caption{}~\label{fig:wedge_layer}
+%	\end{subfigure}
+%	\begin{subfigure}{0.4\linewidth}
+%		\centering
+%		\includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
+%		\caption{}~\label{fig:hex_packing_simple}
+%	\end{subfigure}
+%	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
+%	exhibits wedge-like character. (d) Monomers stack on top of each other to
+%	create columns with short range order, then assemble into pores with 
+%	hydrophilic head groups (blue) facing towards the pore center. (e) The 
+%	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
+%  \end{figure}
 
@@
 
-  % BJC: reworked text
-  \label{rework:purpose}
   A molecular-level understanding of LLC polymer membrane structure, enabled by
@@
 
-  In this paper, we perform molecular modeling of the Col\textsubscript{h}
+  In this chapter, we perform molecular modeling of the Col\textsubscript{h}
   thermotropic (i.e., solvent-free) assembly formed by Na-GA3C11. Compared to the
@@
   construction. Section \ref{S-section:parameterization} 
-  of the SI provides further detail of the parameterization process.
+  of Appendix A provides further detail of the parameterization process.
 
@@
   Simulations of greater than 100 ns show no indicators of progress towards an
-  ordered system (see Section \ref{S-section:self_assembly} of the SI). To bypass
+  ordered system (see Section \ref{S-section:self_assembly} of Appendix A). To bypass
   the slow self-assembly process, we used automated procedures to
   assemble monomers into a structure close to one of a number of hypothesized
-  equilibrium configurations (See Figure \ref{S-fig:build_procedure} of the SI).
+  equilibrium configurations (See Figure \ref{S-fig:build_procedure} of Appendix A).
   These initial structures may result in equilibration into slowly-intercoverting
@@
   and to obtain sufficient resolution when simulating XRD patterns (see further discussion
-  in Section \ref{S-section:monomers_per_column} of the SI).
+  in Section \ref{S-section:monomers_per_column} of Appendix A).
 
@@
   value of 4.12 nm for our initial configurations. A sensitivity analysis of both
-  parameters is presented in the SI, Section
+  parameters is presented in Appendix A, Section
   \ref{S-section:initial_config_dependence}. The distance between vertically
@@
   a third system with an initial spacing of 10 \AA. However this largest spacing
-  yields non-physical behavior which is detailed in the SI, Section
+  yields non-physical behavior which is detailed in Appendix A, Section
   \ref{S-section:initial_dbwl}.
@@
   of $180^\circ/ncol$ where $ncol$ is the number of columns-per-pore. See Figure 
-  \ref{S-fig:stacking} of the SI for a detailed illustration 
+  \ref{S-fig:stacking} of Appendix A for a detailed illustration 
   of the initial configurations in each mode.
@@
   least 400 ns using the Parrinello-Rahman barostat. More equilibration details
-  are given in Section \ref{S-section:equilibration} of the SI.
+  are given in Section \ref{S-section:equilibration} of Appendix A.
 
@@
   SI). The pore spacings calculated in this way are consistent with one half of
-  the $x$ and $y$ box vectors (See Table \ref{S-table:p2p} in the SI). However,
+  the $x$ and $y$ box vectors (See Table \ref{S-table:p2p} in Appendix A). However,
   our method for their calculation does a better job capturing the spread of
@@
   we used the $q_r$ cross-section of 2D-SAXS which was generated from the same
-  sample (Figure \ref{S-fig:2DSAXS} of the SI). Since the d\textsubscript{200} peak is
+  sample (Figure \ref{S-fig:2DSAXS} of Appendix A). Since the d\textsubscript{200} peak is
   partially exposed in the experimental 2D-WAXS pattern, we normalized the
@@
   annulus defined by the bin edges and the z box vector (See Figure \ref{S-fig:rdf_diagram}
-  of the SI).
+  of Appendix A).
 
@@
   measured ion concentration with respect to the volume of the entire unit cell. 
-  More details are provided in the SI, Section \ref{S-section:ionic_conductivity}.
+  More details are provided in Appendix A, Section \ref{S-section:ionic_conductivity}.
 
@@
   We based our cross-linking algorithm on the known reaction mechanism 
-  (Figure \ref{S-fig:xlink_mech} of the SI). The reaction 
+  (Figure \ref{S-fig:xlink_mech} of Appendix A). The reaction 
   takes place at the terminal vinyl groups
@@
   4 additional systems with monomers initially spaced 5 \AA~apart vertically (see
-  Section \ref{S-section:initial_pore_spacing} of the SI for more details on
+  Section \ref{S-section:initial_pore_spacing} of Appendix A for more details on
   sensitivity to initial monomer spacing). We considered the pore-to-pore
@@
   relative to the $xy$ plane to an angle statisically indistinguishable from zero
-  (see Section \ref{S-section:tail_tilt} of the SI).
+  (see Section \ref{S-section:tail_tilt} of Appendix A).
 
@@
   more space to fill causing them to pack nearly isotropically. See Section
-  \ref{S-section:tail_packing} of the SI for a more detailed explanation of the
+  \ref{S-section:tail_packing} of Appendix A for a more detailed explanation of the
   calculation and packing distributions generated from different sections of the
@@
   size in the $z$-direction does not significantly alter $g(z)$ in 
-  Section~\ref{S-section:correlation_functions} of the SI. We calculated the
+  Section~\ref{S-section:correlation_functions} of Appendix A. We calculated the
   equilibrated vertical stacking distance, $\mathit{d}_{equil}$, between monomers
@@
 %  configuration. We tested this hypothesis by annealing systems from high temperatures
-%  as outline in Section~\ref{S-chain_packing} of the SI but saw no improvement
+%  as outline in Section~\ref{S-chain_packing} of Appendix A but saw no improvement
 %  in packing distance.
@@
   the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
-  (see Figure \ref{S-fig:between_pd} of the SI). In this way,
+  (see Figure \ref{S-fig:between_pd} of Appendix A). In this way,
   columns can more easily act 
@@
   since the group extends the system's $\pi$ conjugation~\cite{carey_organic_2011} (see Figure
-  \ref{S-fig:carboxylate_dihedral_rb} of the SI), which is significant even considering
+  \ref{S-fig:carboxylate_dihedral_rb} of Appendix A), which is significant even considering
   possible overestimates of the barrier height in the classical force field.
@@
 %  modest number of occurrences of this scenario, which we quantify in further
-%  detail in the SI, Section \ref{S-section:rdouble}.
+%  detail in Appendix A, Section \ref{S-section:rdouble}.
 
@@
   group below itself. There are a modest number of occurrences of this scenario,
-  which we quantify in further detail in the SI, Section \ref{S-section:rdouble}.
+  which we quantify in further detail in Appendix A, Section \ref{S-section:rdouble}.
 
@@
   region, we used carbon atoms of the monomer tails (See Figure
-  \ref{S-fig:monomer_color_coded} of the SI for a diagram). We averaged the
+  \ref{S-fig:monomer_color_coded} of Appendix A for a diagram). We averaged the
   histograms over the equilibrated portion of the trajectory.  There is a
@@
   monomers in each of the main systems we studied (see Table \ref{S-table:msd} of
-  the SI) and find they are all on the order of
+  Appendix A) and find they are all on the order of
   $10^{-14}~\mathrm{m}^2/\mathrm{s}$. However, since on this timescale, no
@@
   head groups and the ether oxygens which attach the tails to the head group 
-  (see Figure \ref{S-fig:dihedral} of the SI). We exclude the dihedral from the middle tail 
+  (see Figure \ref{S-fig:dihedral} of Appendix A). We exclude the dihedral from the middle tail 
   since it is fundamentally different than the two symmetric outside tails. We 
@@
   relationship using the collective diffusion model\cite{liu_collective_2013} 
-  (see Section \ref{S-fig:conductivity} of the SI). The values calculated by the 
+  (see Section \ref{S-fig:conductivity} of Appendix A). The values calculated by the 
   collective diffusion model agree with Nernst-Einstein values within error, 
@@
   groups on the tails of the monomers were either involved in a cross-linking
-  reaction or were terminated (see Section \ref{S-section:xlink} of the SI for
+  reaction or were terminated (see Section \ref{S-section:xlink} of Appendix A for
   further details of the cross-linking algorithm). We allowed the cross-linked
@@
 
-% BJC: new text
-  \label{rework:conclusion}
   Although exactly reproducing the experimental 2D-WAXS pattern required

### 2020-04-05 Ben_Manuscripts/thesis/transport.tex
Updates to outline and minor changes to figures

@@
 
-  %\graphicspath{{./figs/}}
-  %\graphicspath{{/home/bcoscia/PycharmProjects/LLC_Membranes/Ben_Manuscripts/transport/figures}}
-
   \section{Introduction}
 
-  Membranes capable of separating nm-sized solutes with high selectivity and
-  permeability are highly desirable for a number of applications. For example,
-  separation of salt from seawater or other briny sources can yield potable
-  drinking water.~\cite{fritzmann_state---art_2007} Removal of organic
-  micropollutants, such as personal care products, pesticides and
-  pharmaceuticals, from surface and groundwaters, can have large benefits for
-  public health.~\cite{schwarzenbach_challenge_2006} Finally, one can purify and
-  recover dissolved species present in complex hydraulic fracturing flowback
-  water waste streams which would help mitigate the effects of deep well
-  injection and can be sold for profit.~\cite{dischinger_application_2017}
-
-  All of these separations are possible in part with current commercial
-  membrane separation techniques, but all still suffer from serious drawbacks.
-  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial
-  membrane separations of small molecules.~\cite{warsinger_review_2018} RO
-  membranes are typically dense polymer matrices that separate solutes based on
-  differences in their solubility and permeability in the membrane
-  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
-  selective separations, high feed pressures and thus large amounts of energy are
-  necessary in order to generate a useful permeate
-  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
-  nm-sized pores which can give the same permeate flux as RO with lower applied
-  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
-  size, limiting their selectivity.~\cite{werber_materials_2016}.
-
-  Under the right conditions, amphiphilic molecules can self-assemble into
-  ordered nanostructures that may be capable of performing highly selective
-  separations with permeabilities comparable to
-  NF.~\cite{alexandridis_amphiphilic_2000} The uniform-sized aqueous pores
-  characteristic of these types of systems enforce a molecular-size cut-off,
-  eliminating issues related to the polydisperity of NF
-  pores.~\cite{zhou_supported_2005} In addition to size-exclusion, it may be
-  possible to control the chemical environment within the nanopores by altering
-  the identities of the hydrophilic moieties that form the pores, affording
-  solute-specific separations.~\cite{dischinger_effect_2017}
-
-  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
-  bicontinuous cubic (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
-  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010}
-  When cross-linked, these materials can function as mechanically strong
-  separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} phase
-  has hexagonally packed, straight pores which is the ideal geometry for high
-  throughtput separations. However, the synthesis of H\textsubscript{II}
-  membranes with highly aligned hexagonal mesophases has been a challenge that
-  has been met with limited success and has prevented the material's viability as
-  a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The
-  Q\textsubscript{I} phase consists of a three dimensional network of tortuous
-  and interconnected pores.  It's more facile synthesis has yielded it more
-  success. The latest Q\textsubscript{I} phase membranes have been shown to
-  exhibit selectivities higher than commercial NF and RO membranes with permeabilities
-  higher than commercial RO membranes.~\cite{dischinger_application_2017}
-
-  Although Q\textsubscript{I} membranes have shown promising results, it
-  is not clear how to controllably design them for specific separations
-  beyond what has already been achieved. Dischinger et al. found that they
-  do not separate purely on the basis of size. Empirical modeling revealed
-  correlations between various solute physicochemical properties and 
-  observed solute rejection. Although there was some agreement with their
-  empirical model, it does not offer a sufficiently detailed explanation
-  of governing molecular interactions.~\cite{dischinger_effect_2017}
+%  Membranes capable of separating nm-sized solutes with high selectivity and
+%  permeability are highly desirable for a number of applications. For example,
+%  separation of salt from seawater or other briny sources can yield potable
+%  drinking water.~\cite{fritzmann_state---art_2007} Removal of organic
+%  micropollutants, such as personal care products, pesticides and
+%  pharmaceuticals, from surface and groundwaters, can have large benefits for
+%  public health.~\cite{schwarzenbach_challenge_2006} Finally, one can purify and
+%  recover dissolved species present in complex hydraulic fracturing flowback
+%  water waste streams which would help mitigate the effects of deep well
+%  injection and can be sold for profit.~\cite{dischinger_application_2017} 
+%
+%  All of these separations are possible in part with current commercial
+%  membrane separation techniques, but all still suffer from serious drawbacks.
+%  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial
+%  membrane separations of small molecules.~\cite{warsinger_review_2018} RO
+%  membranes are typically dense polymer matrices that separate solutes based on
+%  differences in their solubility and permeability in the membrane
+%  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
+%  selective separations, high feed pressures and thus large amounts of energy are
+%  necessary in order to generate a useful permeate
+%  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
+%  nm-sized pores which can give the same permeate flux as RO with lower applied
+%  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
+%  size, limiting their selectivity.~\cite{werber_materials_2016}.
+%
+%  Under the right conditions, amphiphilic molecules can self-assemble into
+%  ordered nanostructures that may be capable of performing highly selective
+%  separations with permeabilities comparable to
+%  NF.~\cite{alexandridis_amphiphilic_2000} The uniform-sized aqueous pores
+%  characteristic of these types of systems enforce a molecular-size cut-off,
+%  eliminating issues related to the polydisperity of NF
+%  pores.~\cite{zhou_supported_2005} In addition to size-exclusion, it may be
+%  possible to control the chemical environment within the nanopores by altering
+%  the identities of the hydrophilic moieties that form the pores, affording
+%  solute-specific separations.~\cite{dischinger_effect_2017}
+%
+%  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
+%  bicontinuous cubic (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
+%  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010}
+%  When cross-linked, these materials can function as mechanically strong
+%  separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} phase
+%  has hexagonally packed, straight pores which is the ideal geometry for high
+%  throughtput separations. However, the synthesis of H\textsubscript{II}
+%  membranes with highly aligned hexagonal mesophases has been a challenge that
+%  has been met with limited success and has prevented the material's viability as
+%  a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The
+%  Q\textsubscript{I} phase consists of a three dimensional network of tortuous
+%  and interconnected pores.  It's more facile synthesis has yielded it more
+%  success. The latest Q\textsubscript{I} phase membranes have been shown to
+%  exhibit selectivities higher than commercial NF and RO membranes with permeabilities
+%  higher than commercial RO membranes.~\cite{dischinger_application_2017}
+%
+%  Although Q\textsubscript{I} membranes have shown promising results, it
+%  is not clear how to controllably design them for specific separations
+%  beyond what has already been achieved. Dischinger et al. found that they
+%  do not separate purely on the basis of size. Empirical modeling revealed
+%  correlations between various solute physicochemical properties and 
+%  observed solute rejection. Although there was some agreement with their
+%  empirical model, it does not offer a sufficiently detailed explanation
+%  of governing molecular interactions.~\cite{dischinger_effect_2017}
 
@@
   Python scripts used to set up systems and conduct post-simulation trajectory 
-  analysis (as described below and in the Supporting Information) are available 
+  analysis (as described below and in Appendix B) are available 
   online at \\
@@
   appropriate scripts to use for the subsequent calculations are summarized in 
-  Table~\ref{S-table:python_scripts_transport} of the Supporting Information. We ran all 
+  Table~\ref{S-table:python_scripts_transport} of Appendix B. We ran all 
   MD simulations and energy minimizations using GROMACS 2018.3.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
@@
   conventional simulations. See Section~\ref{S-section:water_content_equil} 
-  of the Supporting Information for an expanded explanation and supporting figures.
+  of Appendix B for an expanded explanation and supporting figures.
 
@@
   ns of simulation (see Figure~\ref{S-fig:5wt_offset_equil} and
-  Figure~\ref{S-fig:10wt_offset_equil} of the Supporting Information). The
+  Figure~\ref{S-fig:10wt_offset_equil} of Appendix B). The
   equilibrated pores contain 72 \% and 69 \% of the total water in the 5 and 10
@@
   each region does not change significantly in either case (see
-  Figure~\ref{S-fig:xlinked_solvation_equilibration} of the Supporting
-  Information). The `wet' equilibration and cross-linking procedures follow the
+  Figure~\ref{S-fig:xlinked_solvation_equilibration} of Appendix B). The `wet' 
+  equilibration and cross-linking procedures follow the
   methods outlined in our previous work.~\cite{coscia_understanding_2019}
@@
   data for generating statistics and a low degree of interaction between solutes (see 
-  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
+  Section~\ref{S-section:solute_interaction} of Appendix B). At each
   insertion point we placed a randomly oriented solute molecule then ran a short 
@@
   ns time lag. Our results are shown to be insensitive to our choice of time lag in 
-  Section~\ref{S-section:lag_sensitivity} of the Supporting Information.
+  Section~\ref{S-section:lag_sensitivity} of Appendix B.
 
@@
   the difference between average hop lengths in and out of the pore. 
-  See Section~\ref{S-section:pore-region} of the Supporting
-  Information for further details on this optimization.
+  See Section~\ref{S-section:pore-region} of Appendix B for further details on this optimization.
 
@@
   bonds~\cite{humphrey_VMD:_1996}. In Section~\ref{S-section:hbond_sensitivity} 
-  of the Supporting Information, we show that our conclusions are insensitive
+  of Appendix B, we show that our conclusions are insensitive
   to this definition within a reasonable range of distances and angles.
@@
   Hydrogen bond lifetimes appear to be distributed according to a power law or an
-  exponential function (see Figure~\ref{S-fig:lifetime_distributions} of the 
-  Supporting Information). A number of researchers provide evidence that supports a 
+  exponential function (see Figure~\ref{S-fig:lifetime_distributions} of
+  Appendix B). A number of researchers provide evidence that supports a 
   power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
@@
   with respect to splines that run through the pore centers. See
-  Section~\ref{S-section:splines} of the Supporting Information for 
+  Section~\ref{S-section:splines} of Appendix B for 
   a graphical illustration. Each spline consists of 10 points, equally
@@
   distal tail regions of the 5 and 10 wt\% water systems respectively. See 
-  Section~\ref{S-section:water_content_equil} of the Supporting Information 
+  Section~\ref{S-section:water_content_equil} of Appendix B 
   for more details on the equilibrations that led to this conclusion. The partition

### 2020-04-05 Ben_Manuscripts/hdphmm/Outline.tex
Added some comments.

@@
     \item Also expressed $G_0 \sim DP(\gamma, H)$
-    %MRS3: This next line is a bit vauge (expresses confidence, closely related)
-    %BJC3: tried to make more clear
-    %MRS4: physically mention what the base distribution is?
     \item The concentration parameter, $\gamma$, expresses one's confidence in the 
     base distribution $H$.
+    \item We use a uniform base distribution.
     \item When $\gamma\to 0$, the first weight of $G_0$, $\beta_1$, approaches 
@@
   %MRS4: remind people what $c$ physically represents here. 
-  \caption{The parameters of the prior on $c$ (black line) should be chosen such
+  \caption{The parameters of the prior on the mean vector, $c$, (black line) should be chosen such
   that the mean levels of each state identified in the trajectory (blue line) lie within
@@
     %MRS4: Do you need to convert the covariance to cylintrical coordinates here before clustereing? 
+    %BJC4: No because I only convert the coordinates to cylindrical and then use 
+    % the inference part of the IHMM to estimate the covariance.
     \item We converted the $x$ and $y$ center-of-mass coordinates to $r$.
@@
    	mean levels are different, especially in the axial direction where solutes could
-   	get trapped along a broad and continuous range of $z$ coordinates. 
+   	gßet trapped along a broad and continuous range of $z$ coordinates. 
   %MRS4: Maybe better to phrase above in terms of the symmetry in z. Why does it matter the range is continuous?
@@
    %MRS4: so no clustering based on transition probablity, correct?
+   %BJC4: not at the moment. That might have been more helpful if I was first-order differencing.
   \end{itemize}
@@
 %    lower values), which implies $2^4$ distinct dynamical behaviors. 
+%MRS5: should be lower-case 's' on silhouette
     \item We used the Silhouette test in order to score the quality of
@@
     %MRS: maybe number (1-4) or label (a-d) the rows as well. 
+    %BJC4: yeah, meant to do that. As it stands, I'm referring to 1 through 4 as bottom through top.
     \item From the top, they describe whether the solute is associated with sodium,
@@
   %BJC3: I still need labels for this plot
+  %BJC4: Also, for some reason, when saving to a PDF, the colorbars are faded. I'll fix this eventually.
+  %MRS5: explicitly state how many states there are, and their colors.
   \begin{figure}
   \includegraphics[width=\textwidth]{mechanism_map.pdf}
-  \caption{}\label{fig:mechanism_map}
+  \caption{We can learn a significant amount of detail about solute motion by viewing 
+  solute trajectories color-coded according to their clustered dynamical behavior alongside
+  plots of the dominant molecular interactions and descriptions of the membrane's local 
+  environment. In the plot above, we show the radial and axial coordinates of a 
+  %MRS5:
+  %chosen
+  single
+  methanol molecule over the course of the equilibrated portion of its MD simulation.
+  Disjoint segments of the same color imply the solute behaves similarly at different 
+  points of the trajectory because their VAR parameters %
+  %MRS5:
+  %are represented by 
+  place them in
+  the same 
+  %BJC4: eventually I'll label the bars and probably put a picture of the monomer with different oxygens labeled
+  cluster. 
+  %MRS5:
+  %Above 
+  On the top of
+the plot are bars which represent different physical interactions and
+  the membrane's local environment as a function of time. The top bar is colored green 
+  at time points where solutes are associated with sodium. Methanol associates
+  with sodium ions relatively rarely. The next bar down is colored when hydrogen bonds exist. Blue slivers
+  correspond to hydrogen bonds donated to the monomer's carboxylate head group. Green slivers
+  corrrespond to  hydrogen bonds donated to the ether linkages between the head groups
+  and tails. Red slivers correspond to hydrogen bonds donated to the oxygens on the ends
+  of the monomer tails. Methanol exhibits significant hydrogen bonding with all parts of
+  the monomer. Which part of the monomer methanol is hydrogen bonds to is heavily correlated
+  to the solute's $r$ coordinate. The bar with the blue gradient represents the local 
+  membrane density based on the solute's ($r$, $z$) coordinate. Darker shades of blue
+  %BJC4: eventually I want some kind of color bar legend
+  correspond to higher membrane densities. The density appears to be higher when methanol
+  motion appears restricted (e.g. from 75 to 550 ns). It is low in areas where methanol's
+  position fluctuates significantly (e.g. from 550 to 700 ns). Finally, the bottom bar
+  simply color-codes the solute's radial distance from the pore center. This information
+  is the same as shown by the radial coordinate but can be a helpful visual aid when
+  studying the other bars.}\label{fig:mechanism_map}
   \end{figure}
-
+  %MRS5: hmm, one sign that someting might be nonideal is the clustering in the light blue state (assuming 1 light blue state), looking at the 75 nm to 550 nm segment and the 900 - 1050 nm segment, the r is quite different (1 vs 3), and the h-bonding patterns are very different (Green vs.
+none).
+So it's not entirely clear these should necessarily be the same state.
+Thoughts?
   One can gain significant chemical intuition just by studying plots like
@@
   \begin{subfigure}{0.35\textwidth}
+  % BJC: I'll bootstrap some errorbars on this by drawing the transition probabilities 
+  % from a dirichlet distribution.
   \includegraphics[width=\textwidth]{dwell_times_MET.pdf}
@@
   \end{subfigure}
-  \caption{}\label{fig:common_states_MET}
+  \caption{We can learn the most about methanol's behavior by studying the dynamics
+  of the states common to the majority of methanol trajectories. In (a), we show representative
+  dynamics of four states that are common to more than half of the solute trajectories. The
+  percentage of trajectories in which they appear are listed between the $r$ and $z$ plots. 
+  All four of these states are exhibited in the trajectory shown in Figure~\ref{fig:mechanism_map}
+  and are colored to match for easy visual comparison. All time series have a mean of zero and are
+  %MRS5: state how much shifted - or maybe plot a dotted line at the zero of each plot?
+  shifted for the purpose of visualizing them. (b) Using the transition probabilities (p), 
+  we estimated the average time spent within each of the states using 1000 simulations of a Bernoulli 
+  process where we continued to draw until transitioning out of the state with probability 1 - p.
+  On average, methanol stay in states 2 and 4 for much longer periods of time than states 1 and 3.
+  This is qualitatively evident in Figure~\ref{fig:mechanism_map}. (c) We can use the understanding
+  from (a) and (b) in order to relate the state parameters to solute motion. States 1 and 3 have
+  large covariances relative to states 2 and 4. Paired with their short dwell times, it is reasonable
+  to hypothesize that states 1 and 3 contribute to hopping behavior while states 2 and 4 
+  correspond to trapped solute behavior. All states have positive autoregressive coefficients (A) in 
+  each dimension which implies motion that is positively correlated to its previous step. States 3 and
+  4 have higher autoregressive coefficients than 1 and 2. This implies that solutes in states 3 and 
+  4 tend to wander more from their mean position in each dimension. This appears to be the case when
+  comparing the behavior of states 2 and 4 in Figure~\ref{fig:mechanism_map}.}\label{fig:common_states_MET}
   \end{figure}
@@
   It is important to understand that the clustered parameter sets are
+  %MRS5: summaries-> averages?
   essentially summaries of many related behaviors. Therefore, the most thorough
+  %MRS5->Figure 6 does have show that there is variance between trajectories. 
   understanding of a specific segment will be gained using descriptive visualizations
@@
   % I need to implement this first to test that hypothesis.
+  %BJC4: I didn't put sodium ion assocaition in this because it's infrequent. 
+  %MRS5: is it correlated with specific states?
+  %BJC4: If I compare to acetic acid or urea, I could add it back. I was thinking of splitting
+  % the pi chart in half with slices corresponding to hbonds on one side and association on the other
   \begin{figure}
@@
   \includegraphics[width=\textwidth]{hbond_pi_charts.pdf}
-  \caption{}\label{fig:hbond_pichart}
+  \caption{With our clustering approach, methanol exhibits similar state behaviors
+  %MRS5: So this is a little counterintuitive, in that the separate states have similar behavior.
+  %MRS5: Are there charts that show what is _different_ about the states as well?  The previous figure
+  %      Shows that they are dynamically different, but this structural pie charge says the existance
+  %      of H-bonding is not the reason . . . 
+  in all regions of the membrane. In all of the common states described in 
+  Figure~\ref{fig:common_states_MET}, methanol, at some point, hydrogen bonds with 
+  each region of the LLC monomer to an appreciable degree. However, methanol frequently
+  is not hydrogen bonded at all.
+  %BJC4: hypothesis yet to be tested. Somehow, I'll incorporate lifetimes into this plot
+  %MRS4: lifetimes would be good!
+  We can learn more by looking at the hydrogen bond lifetime. In states 2 and 4, solutes
+  stay hydrogen bonded for longer periods of time.
+  %MRS5: OK, here is some physical insight - local density is what determines trapping.
+Emphasize the physical mechanisms (wat does and doesn't come out physically because of these analyses) like this more explicitly.
+  %MRS5: can you make other graphs like the H-bond graph? like histogram/pie chart of local density
+  %MRS5: as a function of state?  What about r as a function of state?  what other ways are there to show
+  %MRS5: the characteristics of the states?
+  These longer lifetimes exist because, when hydrogen bonded, the local density is higher, preventing the 
+  bond from breaking so easily. In states 1 and 3, hbonds are fleeting interactions because
+  the surrounding density is low, allowing solutes to move more freely.
+  }\label{fig:hbond_pichart}
   \end{figure}
@@
   \includegraphics[width=\textwidth]{trajectory_realizations_MET.pdf}
-  \caption{}\label{fig:trajectory_realizations_MET}
+  %MRS5: maybe it would be good to put a dotted line through each of the centers of the offset trajectories?
+  %MRS5: Do they really qualitatively reproduce?  the r behavior doesn't really look that similar, as it goes back
+  %      and forth, but not get stuck. 
+  %      Note: it's OK that if the model ends up not being able to describe the system, but we should be clear in 
+  %      what ways it does and doesn't.
+
+  \caption{We can qualitatively reproduce the average behavior of methanol trajectories
+  using our model. Solute trajectories generated by our model (blue) show the same
+  hopping and trapping behavior exhibited by MD (black). The behavior of individual 
+  MD trajectories tend to show wider variability than our model's realization because
+  the model effectively represents the average behavior of the MD trajectories. This 
+  implies that much longer simulations might be necessary in order to obtain a set
+  of trajectories that explore state space to the same extent.
+  %BJC4: this observation is how I got the idea to calculate MSD by parameterizing
+  % individual trajectories  
+  %BJC4: Also note that I'm not currently happy with how I generate the radial dimension. 
+  %MRS5: how do you do that currently? We talked about generating dynamics in x, y, and z, 
+  %MRS5: (should be same parameters for x and y, because of symmetry), and then converting to r. 
+  %MRS5: could make this more clear in the methods. 
+  % Improvements will not affect z or the MSD because the VAR parameters won't change except for c
+   }\label{fig:trajectory_realizations_MET}
   \end{figure}
@@
     % procedure and it make sense to me.
+    % MRS3: Thinking out loud - if 4/24 trajectories are big, then 
+    % (5/6)^24 = 0.013 will contain none of the 'big' trajectories.
+    % 24*(1/6)*(5/6)^23 = 0.060 will contain 1.
+    % C(24,2)*(1/6)^2*(5/6)^22 = 0.139 will contain 2
+    % C(24,3)*(1/6)^3*(5/6)^21 = 0.204 will contain 3 
+    % C(24,4)*(1/6)^4*(5/6)^20 = 0.214 will contain 4
+    % C(24,5)*(1/6)^5*(5/6)^19 = 0.171 will contain 5
+    % C(24,6)*(1/6)^6*(5/6)^18 = 0.108 will contain 6
+    % MRS5: so I guess it makes sense that the median bootstrap trajectory will have 4 big trajectories,
+    % MRS5: and that the 1 sigma line on the lower end will be ones with 2 'big' trajectories.
+    % MRS5: You could also plot the 95% confidence intervals
     % BJC3: I could show how it's possible to get good agreeement with MD by only
@@
   \end{subfigure}
+  \caption{The MSDs predicted based on 1000 realizations of our model (blue) tend to underpredict
+  the MSDs based on the MD trajectories (black). Due to the variability in solute behavior across MD trajectories,
+  as demonstrated in Figure~\ref{fig:trajectory_realizations_MET}, there are several 
+  individual solute MSD curves that are significantly higher than the rest and drive up the
+  mean of the MSD. If we remove those trajectories from the MSD calculation, we obtain 
+  estimates much closer to the IHMM estimate.(I haven't done it yet, but could plot a third curve
+  with outlier removed). Acetic acid, has no obvious outliers which is consistent with our model's
+  prediction which lies within the 1$\sigma$ confidence interval of MD after a 1000 ns time lag.}\label{fig:msds}
   \end{figure}

### 2020-04-07 Ben_Manuscripts/hdphmm/Outline.tex
Reworking outline with radial clusters

@@
   	distinguishing these behaviors.   	
-  	\item Clustering the behaviors helps us to tell a coherent story which
-  	emphasizes those interactions which most heavily influence solute transport.
-  	\item This analysis approach helps us to break down the very complex behavior
-  	exhibited by solutes over long MD trajectories into discrete categories.
+  	\item The following approach to analysis demonstrates how one can break 
+  	down the very complex behavior exhibited by solutes over long MD trajectories 
+  	into discrete categories.
+%  	\item Clustering the behaviors helps us to tell a coherent story which
+%  	emphasizes those interactions which most heavily influence solute transport.
+	\item Further, we can use the IHMM in order to generate stochastic trajectories,
+	with dynamics similar to MD, so that we can estimate macroscopic transport
+	properties.
   \end{itemize}
@@
 
-  %BJC3: obviously can use a better thesis.
-  We showcase this modeling approach by example. 
+  We applied the IHMM to all trajectories of each of the four solutes studied.
+  \begin{itemize}
+    \item Based on our choice of clustering, we identified over 30 distinct dynamical
+    modes for each solute.
+    \item Many of these modes are sampled very infrequently and thus do not merit significant study.
+    \item In this section, we explore a subset of this data, focusing on the states
+    and dominant interactions most common to solute trajectories. 
+  \end{itemize}
+
+  \noindent Methanol exhbits a range of dynamic behavior.
   \begin{itemize}
@@
     dynamics are most consistent, which implies that this particular methanol 
-    trajctory exhibits 6 distinct dynamical behaviors. 
+    trajctory exhibits 8 distinct dynamical behaviors (in order of their first appearance,
+    they are colored dark yellow, red, light blue, light green, orange, blue, teal and lime green). 
     \item The solute timeseries are coupled with color coded bars which describe the
     solute's local environment and physical interactions that it undergoes at that
-    time frame.
-    %MRS: maybe number (1-4) or label (a-d) the rows as well. 
-    %BJC4: yeah, meant to do that. As it stands, I'm referring to 1 through 4 as bottom through top.
+    trajectory frame.
     \item From the top, they describe whether the solute is associated with sodium,
-    whether the solute is hydrogen bonding with the monomer as well as what part of
-    the monomer it is hydrogen bonding to, the local number density surrounding the
-    solute and the radial location of the solute with respect to the nearest pore
-    center (this information is redundant but can be a useful visual aid). %BJC3: still debating removing that bar
-  \end{itemize}
-
-  %BJC3: I still need labels for this plot
-  %BJC4: Also, for some reason, when saving to a PDF, the colorbars are faded. I'll fix this eventually.
-  %MRS5: explicitly state how many states there are, and their colors.
+    whether the solute is hydrogen bonding with the monomer as well as to what part of
+    the monomer it is hydrogen bonding, and finally, the local number density 
+    surrounding the solute. 
+    %and the radial location of the solute with respect to the nearest pore
+    %center (this information is redundant but can be a useful visual aid).
+  \end{itemize}
+
   \begin{figure}
-  \includegraphics[width=\textwidth]{mechanism_map.pdf}
-  \caption{We can learn a significant amount of detail about solute motion by viewing 
+  \centering
+  \begin{subfigure}{0.75\textwidth}
+  \includegraphics[width=\textwidth]{mechanism_map.png}
+  \caption{}
+  \end{subfigure}
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{monomer_oxygens.png}
+  \caption{}
+  \end{subfigure}
+  \caption{(a) We can learn a significant amount of detail about solute motion by viewing 
   solute trajectories color-coded according to their clustered dynamical behavior alongside
   plots of the dominant molecular interactions and descriptions of the membrane's local 
-  environment. In the plot above, we show the radial and axial coordinates of a 
-  %MRS5:
-  %chosen
-  single
+  environment. In the plot above, we show the radial and axial coordinates of a single
   methanol molecule over the course of the equilibrated portion of its MD simulation.
   Disjoint segments of the same color imply the solute behaves similarly at different 
-  points of the trajectory because their VAR parameters %
-  %MRS5:
-  %are represented by 
-  place them in
-  the same 
-  %BJC4: eventually I'll label the bars and probably put a picture of the monomer with different oxygens labeled
-  cluster. 
-  %MRS5:
-  %Above 
-  On the top of
-the plot are bars which represent different physical interactions and
-  the membrane's local environment as a function of time. The top bar is colored green 
-  at time points where solutes are associated with sodium. Methanol associates
-  with sodium ions relatively rarely. The next bar down is colored when hydrogen bonds exist. Blue slivers
+  points of the trajectory because their VAR parameters place them in the same cluster. 
+  There are eight distinct dynamical modes exhibited by this trajectory. In order
+  of their first appearance, they are colored dark yellow, red, light blue, light green,
+  orange, blue, teal and lime green. On the top of the plot are bars which represent different
+  physical interactions and the membrane's local environment as a function of time. The top 
+  bar is colored green at time points where solutes are associated with sodium. Methanol 
+  associates with sodium ions relatively infrequently. The next bar down is colored when hydrogen
+  bonds exist. The colors match the enlarged oxygen atoms highlighted in (b). Blue slivers
   correspond to hydrogen bonds donated to the monomer's carboxylate head group. Green slivers
@@
   of the monomer tails. Methanol exhibits significant hydrogen bonding with all parts of
-  the monomer. Which part of the monomer methanol is hydrogen bonds to is heavily correlated
-  to the solute's $r$ coordinate. The bar with the blue gradient represents the local 
+  the monomer. Which part of the monomer methanol hydrogen bonds to is heavily correlated
+  to the solute's $r$ coordinate. Finally, the bar with the blue gradient represents the local 
   membrane density based on the solute's ($r$, $z$) coordinate. Darker shades of blue
-  %BJC4: eventually I want some kind of color bar legend
   correspond to higher membrane densities. The density appears to be higher when methanol
-  motion appears restricted (e.g. from 75 to 550 ns). It is low in areas where methanol's
-  position fluctuates significantly (e.g. from 550 to 700 ns). Finally, the bottom bar
-  simply color-codes the solute's radial distance from the pore center. This information
-  is the same as shown by the radial coordinate but can be a helpful visual aid when
-  studying the other bars.}\label{fig:mechanism_map}
+  motion is restricted (e.g. from 75 to 550 ns). It is relatively low in areas where methanol's
+  position fluctuates significantly (e.g. from 550 to 700 ns). 
+  %Finally, the bottom bar
+  %simply color-codes the solute's radial distance from the pore center. This information
+  %is the same as shown by the radial coordinate but can be a helpful visual aid when
+  %studying the other bars.
+  }\label{fig:mechanism_map}
   \end{figure}
-  %MRS5: hmm, one sign that someting might be nonideal is the clustering in the light blue state (assuming 1 light blue state), looking at the 75 nm to 550 nm segment and the 900 - 1050 nm segment, the r is quite different (1 vs 3), and the h-bonding patterns are very different (Green vs.
-none).
-So it's not entirely clear these should necessarily be the same state.
-Thoughts?
-  One can gain significant chemical intuition just by studying plots like
+
+  \noindent One can gain useful chemical intuition just by studying plots like
   Figure~\ref{fig:mechanism_map}.
@@
     state changes during that time period and red slivers in the bar above.
+    \item Signficant hops in the $z$ direction appear to be described by the blue
+    state.
+    \item After entering the blue state ca. 850 ns, methanol appears to jump
+    signficantly in the $z$ direction from a hydrogen bonded state with the ether 
+    linkages to a hydrogen bonded state with a head group in a monomer below it.
   \end{itemize}
@@
 
-  We may learn the most by studying the dynamical modes common to the majority of 
+  \noindent It is clear that there is a wealth of information in these plots. 
+  \begin{itemize}
+    \item One can analyze each segment sequentially and form a clear picture
+    of this instance of methanol's behavior without the need to visulize
+    the traejectory with software like VMD.
+    \item However, a more general understanding of methanol's average behavior
+    is necessary in order to formulate LLC membrane design principles.
+  \end{itemize}
+
+  %BJC: I'm not sure whether to spell out the numbers or not. 'six state' versus '6 states'; 'eight out of 24' or '8 out of 24'
+  % 'State one or State 1' 
+  \noindent We may learn the most by studying the dynamical modes common to the majority of 
   the solute trajectories.
   \begin{itemize}
-    \item Using the IHMM, we identified 13 total dynamical modes exhibited by 
+    \item Using the IHMM, we identified 33 total dynamical modes exhibited by 
     methanol. 
-    \item Of those, 4 appear in at least 50 \% of the methanol trajectories, and
-    2 of them appear in over 90 \% of the methanol trajectories.
+    \item Of those, only six states appear in a third (8 out of 24) or more methanol 
+    trajectories, and 3 of them appear in over 50 \% of the methanol trajectories.
+    \item 12 of the detected states are shared by two or less methanol trajectories.  % 23 in 3 or less -- not sure which is better to say
     \item In Figure~\ref{fig:common_states_MET_lines}, we plot representative dynamics
-    of each of the 4 prevelant states.
-    \item Based on their self-transition probabilities, we estimated the average 
-    time spent by each solute in each state (Figure~\ref{fig:dwell_times_MET}).
-    \item States 2 and 4 have long dwell times relative to states 1 and 3 because
+    of each of the six states which we determined to be prevelant.
+    \item We also chose to study a seventh state, which only appears in three out of
+    24 trajectories, because methanol experiences very long periods of entrapment
+    while in this state. Long trapping events, even if they are relatively rare, will
+    have a significant influence on solute flux.
+    \item No trajectory contains all seven states. However, the trajectory in 
+    Figure~\ref{fig:mechanism_map} exhibits all modes except states 6 and 7.
+    \item The states in Figure~\ref{fig:common_states_MET} are colored to match
+    states that also appear in Figure~\ref{fig:mechanism_map}.
+  \end{itemize}
+
+  \noindent We can begin to dissect the dynamics of each state by studying their parameters.
+  \begin{itemize}
+    \item States 1, 3 and 5 have radial means near 1 nm or less (see y axis of $r$ direction plot in
+    Figure~\ref{fig:common_states_MET_lines}), which suggest that they occur
+    close to the pore centers. 
+    \item States 2, 4, 6 and 7 occur well within the tail region of the membrane.
+    \item States 1 and 2 have higher covariances in both the axial and radial
+    directions compared to all other states.
+    \item Covariance in each dimension appears to have a strong correlation.
+    \item States 3 and 5 as well as states 4, 6 and 7 are primarily distinguished based
+    on their autoregressive coefficients, A. 
+    \item Higher values of A generally lead to more wandering about the state mean.
+    \item One could argue that the parameters of states 3--7 are actually very close which
+    suggests that solutes might behave alike in topologically distinct regions of the 
+    membrane.
+  \end{itemize}
+
+  Despite some similarity in their VAR parameters, the length of time spent in states 3--7 
+  appears to be dependent on the solute's radial location.
+  \begin{itemize}
+    \item Based on the self-transition probabilities, we estimated the average time
+    spent by each solute in each state (Figure~\ref{fig:dwell_times_MET}).
+    \item States 3, 5 and 7 have long dwell times relative to the rest because
     they have high self-transition probabilities.
-    \item States 1 and 3 show large fluctuations relative to the other states owing
-    to larger covariances in both the axial and radial dimensions. (Figure~\ref{fig:A_sigma_scatter_MET})
-    \item States 1 and 2 have lower autoregressive coefficients relative to states
-    3 and 4.
-    \item All of these states are present in Figure~\ref{fig:mechanism_map} and colored
-    accordingly.
+    \item Somewhat surprisingly, both states 3 and 5 correspond to solutes located close to
+    a pore center, where one might expect solute motion to be less restricted.
+    \item Although solutes in states 4 and 6 are in the viscous tail region, their
+    dwell times are only intermediate. This could be due to imhomogeneity in the
+    tail region which causes transitions between many different trapped states but
+    with litle net effect on solute MSD. 
+    \item However, there are instances of states within the tail region with dwell 
+    times that exceed 100--200 ns, as shown by our inclusion of state 7.
+%    \item These long dwell times have a significant effect on dynamics and are
+%    worth studying.
+    \item There are no other states with dwell times longer than state 5 in the pore 
+    region.
+  \end{itemize}
+
+  \noindent States 1 and 2 exhibit the shortest dwell times of the states studied.
+  \begin{itemize}
+      \item This is consistent with the trajectory in Figure~\ref{fig:mechanism_map}.
+      \item State 2 is the shortest lived state, appearing to bridge other tail region
+      states. 
+      \item State 1 appears to represent a significant hopping state. 
+      \item It has a high covariance and occurs near the pore center, where there is
+      less obstruction to solute motion.
+      \item It's dwell time of ca. 8 ns, suggests that solutes stay in this highly
+      mobile state for long enough to displace signficantly.
   \end{itemize}
@@
   % from a dirichlet distribution.
-  \includegraphics[width=\textwidth]{dwell_times_MET.pdf}
-  \caption{}\label{fig:dwell_times_MET}
   \includegraphics[width=\textwidth]{A_sigma_scatter_MET.pdf}
   \caption{}\label{fig:A_sigma_scatter_MET}
+  \includegraphics[width=\textwidth]{dwell_times_MET.pdf}  %BJC5: maybe better as 95 % confidence rather than mean
+  \caption{}\label{fig:dwell_times_MET}
   \end{subfigure}
   \caption{We can learn the most about methanol's behavior by studying the dynamics
-  of the states common to the majority of methanol trajectories. In (a), we show representative
-  dynamics of four states that are common to more than half of the solute trajectories. The
-  percentage of trajectories in which they appear are listed between the $r$ and $z$ plots. 
-  All four of these states are exhibited in the trajectory shown in Figure~\ref{fig:mechanism_map}
+  of the states common to many of the methanol trajectories. In (a), we show representative
+  dynamics of six states that are common to more than one third of the solute trajectories. 
+  The $y$-axis labels of the $r$ coordinate plot specify the radial mean of each clustered 
+  state. The percentage of trajectories in which the states appear are labeled to the right of
+  the $r$ plots. States 1--5 appear in the trajectory shown in Figure~\ref{fig:mechanism_map}
   and are colored to match for easy visual comparison. All time series have a mean of zero and are
-  %MRS5: state how much shifted - or maybe plot a dotted line at the zero of each plot?
-  shifted for the purpose of visualizing them. (b) Using the transition probabilities (p), 
-  we estimated the average time spent within each of the states using 1000 simulations of a Bernoulli 
-  process where we continued to draw until transitioning out of the state with probability 1 - p.
-  On average, methanol stay in states 2 and 4 for much longer periods of time than states 1 and 3.
-  This is qualitatively evident in Figure~\ref{fig:mechanism_map}. (c) We can use the understanding
-  from (a) and (b) in order to relate the state parameters to solute motion. States 1 and 3 have
-  large covariances relative to states 2 and 4. Paired with their short dwell times, it is reasonable
-  to hypothesize that states 1 and 3 contribute to hopping behavior while states 2 and 4 
-  correspond to trapped solute behavior. All states have positive autoregressive coefficients (A) in 
-  each dimension which implies motion that is positively correlated to its previous step. States 3 and
-  4 have higher autoregressive coefficients than 1 and 2. This implies that solutes in states 3 and 
-  4 tend to wander more from their mean position in each dimension. This appears to be the case when
-  comparing the behavior of states 2 and 4 in Figure~\ref{fig:mechanism_map}.}\label{fig:common_states_MET}
+  shifted to put the mean in line with the $y$-axis labels for the purpose of visualizing them. 
+  (b) We can begin to understand the solute behaviors demonstrated in (a) by understanding their VAR 
+  parameters. States 1 and 2 have higher covariances in both the axial and radial directions compared
+  to all other states. This should lead to signficant solute displacement. Covariance in each dimension
+  appears to have a strong correlation. States 3--6 all have relatively low covariances, which may
+  be characteristic of trapped states. They are primarily distinguished based on the magnitude of their 
+  autoregressive coefficients, A, and radial means. Higher values of A imply motion which wanders 
+  more about the mean. States 1, 3 and 5 have radial means near 1 nm or less, which suggest that they
+  occur close to the pore centers. States 2, 4 and 6 occur well within the tail region of the membrane.
+  (c) Using the transition probabilities (p), we estimated the average time spent within each 
+  of the states using 1000 simulations of a Bernoulli process where we continued to draw until transitioning
+  out of the state with probability 1 - p. Of the prevelent states, states 1 and 
+  2 exhbit the shortest dwell times alongside their high covariances. States 3 and 6 have the longest dwell
+  times where methanol appears to be trapped near the pore center.   
+  }\label{fig:common_states_MET}
   \end{figure}
+
+  Our speculation so far is based purely on the parameters of our model compared to 
+  a single methanol trajectory.
+  \begin{itemize}
+    \item While we may be able to further corroborate our arguments by analyzing more
+    individual trajectories, it is more useful to correlate the state behavior with
+    solute-membrane interactions.
+  \end{itemize}
+
+  The types of hydrogen bonding undergone by solutes is dependent on radial
+  location (see Figure~\ref{fig:hbond_pi_chart}).
+  \begin{itemize}
+    \item States with radial means near 1 nm or less (states 1, 3 and 5) typcially
+    hydrogen bond with the monomer carboxylate groups and ether linkages.
+    \item States with radial means greater than 1 nm (states 2, 4, 6 and 7) tend 
+    to hydrogen bond with the monomer tails.
+    \item In the past we've shown how there is a gradual transition from the
+  	hydrophilic to hydrophobic region in these membranes, meaning the monomer
+  	location is not tightly bound in $r$.
+  	\item Therefore, there are instances of hydrogen bond interactions that one
+  	might consider uncharacteristic based on the state's radial mean.
+  \end{itemize}
+
+  States which exhibit longer dwell times have longer hydrogen bond lifetimes.
+  \begin{itemize}
+    \item States 3--7 have significantly longer hydrogen bond lifetimes than states
+    1 and 2. 
+    \item It makes physical and mathematical sense that states 1 and 2 should not 
+    stay trapped by hydrogen bonding for long periods because they typically take large
+    hops as communicated by their large covariances.
+    \item In the tail states, hydrogen bond lifetimes appear to increase with 
+    their dwell times.
+    \item However, in the pores, this is not necessarily a linear relationship. 
+    \item For example, state 5 has the lowest hydrogen bond lifetime of states 3--6
+    despite having the second longest dwell times. 
+  \end{itemize}
+
+  The local density experienced by solutes may have an impact on the length of solute 
+  entrapment.
+  \begin{itemize}
+    \item On average, solutes in state 5 are surrounded by an above average number of
+    particles. 
+    \item Based on its radial location and preference towards hydrogen bonding
+    with the ether linkages, it is reasonable to assume that while in state 5, methanol
+    spends most of its time just outside the pore region, sandwiched between the 
+    monomer head groups. 
+    \item Although state 5 hydrogen bonds break more frequently than one might expect for 
+    a state with long dwell times, it is possible that the solute's dense surroundings
+    prevent it from wandering off before the hydrogen bonding interaction can be
+    recovered.
+    \item This may explain the behavior of methanol in state 5 of the trajectory in
+    Figure~\ref{fig:mechanism_map} where the solute's center of mass appears to move
+    more freely about its mean than other trapped states.
+    \item The data suggests that methanol molecules in state 3 lie closer to the pore
+    center than state 5 because they tend to hydrogen bond most frequently with 
+    the carboxylate groups.
+    \item Methanol molecules which experience state 3 are subject to a lower density 
+    local environment and rely more heavily on hydrogen bonding interactions, 
+    evidenced by their longer lifetimes, to stay trapped.
+  \end{itemize}
+
+  States describing behavior in the tail region show a direction relationship between 
+  hydrogen bond lifetimes and local density.
+  \begin{itemize}
+    \item Methanol molecules which experience state 2 are in a low density region of the
+    tails where they can easily break free of hydrogen bonds.
+    \item Methanol molecules in states 4 and 6 have hydrogen bond lifetimes that are similar
+    to the mean dwell times, which suggests
+    \item Finally, methanol molecules trapped in state 7 are in the densest region of all
+    states studied. It is likely difficult for methanol to esacpe these high density regions
+    and its position is further stabilized via hydrogen bonding.
+  \end{itemize}
 
@@
   \centering
+  \begin{subfigure}{0.54\textwidth}
   \includegraphics[width=\textwidth]{hbond_pi_charts.pdf}
+  \caption{}\label{fig:hbond_pi_charts}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{hbond_lifetimes_density_MET.pdf}
+  \caption{}\label{fig:hbond_lifetimes_density_MET}
+  \end{subfigure}
   \caption{With our clustering approach, methanol exhibits similar state behaviors

### 2020-04-07 Ben_Manuscripts/thesis/intro.tex
Reworking outline with radial clusters

@@
   \includegraphics[width=\textwidth]{figs/membrane_separation_size_regimes.pdf}
-  \caption{Caption of the future}\label{fig:size_regimes}
+  \caption{Choosing a membrane separation technology is entirely dependent on the
+  size of the particle to be removed. The diagram provides examples of the types 
+  of particles that each class of membranes is able to remove. Microfiltration (MF) 
+  membranes contain pores with diameters ranging from 100-10000 nm and can separate
+  large particles like bacteria and protozoa.~\cite{ma_functionalized_2014}
+  Ultrafiltration (UF) membranes have pore diameters of about 5-500 nm and are 
+  useful for the separation of sugars, proteins, viruses and colloidal 
+  materials.~\cite{yanful_ultrafiltration_2009} Nanofiltration (NF) membranes have
+  pores on the order of 1 nm in diameter and can be used for the separation of 
+  small organic molecules and charged species.~\cite{van_der_bruggen_review_2003}
+  Reverse osmosis (RO) membranes are dense amorphous polymers with tortuous 
+  pathways formed by collapsed polymer networks. Their dense polymer architecture 
+  rejects all solutes to a high degree except for water making them useful for 
+  separating hydrated ions from water.~\cite{warsinger_review_2018}
+  }\label{fig:size_regimes}
   \end{figure}
@@
   \includegraphics[width=\textwidth]{figs/lc_phases.pdf}
-  \caption{}\label{fig:lc_phases}
+  \caption{The amphiphilic character of liquid crystal monomers drives their
+  self-assembly into various nanostructured phases with uniform sized pores. 
+  The hydrophilic components of the monomers line the aqueous pores, offering
+  potential for selective interactions with passing solutes. The monomer on 
+  the top left will form the inverted hexagonal (H\textsubscript{II})
+  phase which is composed of aligned cylindrical pores packed in a hexagonal 
+  array. This geometry is theoretically ideal for high throughput transport. 
+  The monomer on the right will for the type I bicontinuous cubic phase
+  (Q\textsubscript{I}) in either the Ia3d (gyroid) or Pn3m (diamond) space group.
+  Although the Q\textsubscript{I} phase has a much more tortuous network of 
+  pores than the H\textsubscript{II}, which should lower its relative permeabily,
+  its synthesis is much more practical because it does not require alignment of
+  the nanostructured mesophases.
+  }\label{fig:lc_phases}
   \end{figure}
-
-  %BJC: figure TBD here showing each monomer and the phase they form
 
@@
   order to understand solute transport within LLC membranes with molecular 
-  detail. Before diving into atomistic model, we offer a brief survey of 
-  the most popular macroscopic treatments in order to highlight how an
-  atomistic model may be better suited to understanding how to design LLC
-  %TODO
-
-  %MRS3: one issue is that after this paragraph, it's not entirely
-  %clear where you are going.  This describes common models, but not
-  %how your research is placed in respect to them.
-  %BJC3: Added above connecting paragraph
+  detail. Before diving into an atomistic model, we offer a brief survey of 
+  the most popular macroscopic treatments in order to highlight how a 
+  nanoscopic perspective offered by atomistic modeling may be better suited to 
+  understanding how to design the next generation of LLC membranes.
 
@@
   where $L_i$ is a coefficient of proportionality.~\cite{wijmans_solution-diffusion_1995}
-  $L_i$ is an intrinsic materials property dependent on ... % Wijman's doesn't say. I don't want to speculate. Get book he referenced from library
-      %MRS2: mention what L depends on molecularly (even if uncalculatable)
-  Chemical potential gradients can be induced by concentration, pressure, temperature
+  $L_i$ is an intrinsic materials property dependent on the chemical makeup of
+  the membrane and usually determined via experiment. Chemical potential gradients
+  can be induced by concentration, pressure, temperature
   and electromotive forces. We will limit our discussion to concentration and pressure

### 2020-04-08 Ben_Manuscripts/hdphmm/Outline.tex
New updates to outline

@@
   	vector $\mathbf{c}$ and a white noise term $\mathbf{e}_t$.~\cite{hamilton_time_1994}
-        %MRS2: mean is zero in Z, is it necessarily in R (I realize we've talked about this before, but wanted to get the clarification in text)
-    %BJC2: The mean I'm talking about below is different than you are describing above.
-    % The multivariate Gausian noise is coming from N(0, \Sigma)
   	\item We assumed $\mathbf{e}_t$ to be multivariate Gaussian noise, with mean zero and
@@
     %MRS4: yes, she how she wants to cite it.
-    %MRS3: be a bit more specific about what the criteria were for convergence.
-    %BJC3: See if that's better
-    %MRS4: But what quantitative criteria did you use to determine convergence?
     \item Parameter estimation is iterative. Therefore, we looked for convergence 
@@
     Equation~\ref{eqn:var}.
+    \item We detected equilibration of the parameters using the module 
+    \texttt{pymbar.timeseries.detect\_equilibration} on the time series of 
+    parameter estimates. 
     \item Plots illustrating parameter convergence are available in the SI.
@@
   \end{itemize}
-
-  % BJC3: I tried again with this paragraph above. I want to set up the idea that we
-  % are performing this somewhat complex procedure for a good reason before jumping
-  % straight into it.
-  %MRS3: be more specific - i.e. describe what are the ways you are going to apply it. 
-%  There are many ways one can apply the IHMM algorithm to timeseries data. 
-%  \begin{itemize}
-%    %MRS3: it's not as many as possible, but identify one's supported by the data, right?
-%    \item We begin by trying to identify as many distinct states as possible
-%    in each solute trajectory and then take advantage of the system's cylindrical
-%    symmetry in order to cluster the parameter sets into an interpretable number
-%    of states.
-%    %MRS3: not clear why this is the case?
-%    \item Having a large number of states gives more reliable clustering results.
-%%    \item We believe the subsequent procedure is best suited for our data
-%%    because it can clearly distinguish different dynamical behavior, it takes
-%%    advantage of the system's cylindrical symmetry and represents distinct
-%%    dynamics in an interpretable number of states.
-%  \end{itemize}
 
@@
     the solutes.
-    \item We work in cylindrical coordinates since each pore is cylindrical
-    and we expect solutes to exhibit radially symmetric dynamics.
-  \end{itemize}
-
-  We start by applying the IHMM algorithm to 3D solute center-of-mass coordinate 
+    \item Ultimately, we work in cylindrical coordinates since each pore is a 
+    cylinder where we expect solutes to exhibit radially symmetric dynamics.
+  \end{itemize}
+
+  We start by applying the IHMM algorithm to the 3D solute center-of-mass coordinate 
   trajectories transformed relative to the closest pore center.
@@
   %but would be good to make that explicit - ``i.e. we need to make sure it doesn't jump too far'')
+  %BJC5: preserving z-axis symmetry isn't needed yet at this stage. I use the
+  % means in z in order to distinguish states (specifically estimating the c vector).
+  % I get the radial means this way. Then just ignore z later.
   \includegraphics[width=0.2\textwidth]{cartesian_cylinder.pdf}
@@
 
-  We applied the IHMM to each of the 24 solute trajectories independently.
+  \noindent We applied the IHMM to each of the 24 solute trajectories independently.
   \begin{itemize}
@@
 
-  The states identified by the IHMM are heavily influenced by the Gaussian prior
+  % BJC5: For the paper, this paragraph and figure might be better suited for the supporting information
+  % BJC5: maybe even for the thesis
+  \noindent The states identified by the IHMM are heavily influenced by the Gaussian prior
   placed on $\mathbf{c}$ in Equation~\ref{eqn:var}.
@@
   % the parameterization process. It might be bunch of plots stacked on each other.
-  %BJC2: More labels might be useful if not cluttered
+  %BJC2: More labels would be useful if not cluttered
   \begin{figure}
@@
   \includegraphics[width=\textwidth]{prior_guesses.pdf}
-  %MRS4: remind people what $c$ physically represents here. 
-  \caption{The parameters of the prior on the mean vector, $c$, (black line) should be chosen such
+  \caption{The parameters of the prior on the mean vector, $c$, (black line), which
+  represents the coordinates at which solute are trapped, should be chosen such
   that the mean levels of each state identified in the trajectory (blue line) lie within
@@
     % symmetric distributions, it's essentially the same.
-    \item We detected equilibration of the parameters using the module 
-    \texttt{pymbar.timeseries.detect\_equilibration} on the time series of 
-    parameter estimates. 
+    %BJC5: moved following point to earlier in methods.
+%    \item We detected equilibration of the parameters using the module 
+%    \texttt{pymbar.timeseries.detect\_equilibration} on the time series of 
+%    parameter estimates. 
     \item We found the equilibration time point of each component of the 
@@
 
-  We clustered like parameter sets in order to reduce the state space to
+  \noindent We clustered like parameter sets in order to reduce the state space to
   a more easily interpretable size.
@@
    	\item Many of these states exhibit very similar dynamical behavior except their
-   	mean levels are different, especially in the axial direction where solutes could
-   	gßet trapped along a broad and continuous range of $z$ coordinates. 
-  %MRS4: Maybe better to phrase above in terms of the symmetry in z. Why does it matter the range is continuous?
+   	mean levels are different.
   \end{itemize}
@@
   % this is the one I'm going with for now.
-  We clustered based on the two diagonal entries of $A$ and the two diagonal entries 
-  of $\Sigma$.
+  We clustered based on the two diagonal entries of $A$ and $\Sigma$ as well as the
+  radial means, $\mu_r$, for a total of 5 variables.
   \begin{itemize}
@@
    %MRS4: suggest translating them here into solute behavior for the reader!
-   \item We also chose to cluster the diagonals of each matrix independently before
-   combining the clusters to assign final state labels. 
+   \item We also chose to cluster the diagonals of each matrix and the radial means
+   independently before combining the clusters to assign final state labels. 
    \item If we divide the total states into $m$ clusters based on the diagonal entries
-   of $A$ and, separately, $n$ clusters based on the diagonal entries of $\Sigma$,
-   then there are a total of $mn$ possible cluster combinations.
+   of $A$, $n$ more clusters based on the diagonal entries of $\Sigma$, and $k$ clusters
+   based on $\mu_r$, then there are a total of $mnk$ possible cluster combinations.
    \item This allows slightly more flexibility in the total number of states compared
-   to clustering on all four features at once, since there can be up to, but not 
-   necessarily exactly, $mn$ states. 
+   to clustering on all five features at once, since there can be up to, but not 
+   necessarily exactly, $mnk$ states. 
    %MRS4: so no clustering based on transition probablity, correct?
@@
 %    lower values), which implies $2^4$ distinct dynamical behaviors. 
-%MRS5: should be lower-case 's' on silhouette
-    \item We used the Silhouette test in order to score the quality of
-    clusters as a function of the number of clusters chosen.
-    \item For our data, the Silhouette test generally favors the lowest number
+    \item We used the silhouette test in order to score the quality of
+    clustering as a function of the number of clusters chosen.
+    \item For our data, the silhouette test generally favors the lowest number
     of clusters possible (see Supporting Information).
@@
     modeling that we discuss later on.
-    \item We aimed to maintain the highest Silhouette score, and thus lowest
+    \item We aimed to maintain the highest silhouette score, and thus lowest
     number of clusters, possible while verifying that visually distinct 
@@
     \item Based on these guidelines, we decided to group the $A$ and $\Sigma$
-    parameters into five clusters each. 
-	\item Of the 25 distinct states allowed by this formulation, the solutes
-	in this study clustered into 13--18 distinct clusters.
-  \end{itemize}
-
-  We remapped the state sequence based on the cluster assignments and
+    parameters into five clusters each and the radial means into three clusters. 
+	\item Of the 75 distinct states allowed by this formulation, the solutes
+	in this study clustered into 30--33 distinct clusters.  %BJC5: need to check these numbers
+	\item While this may seem like a high number of states, many are sampled
+	infrequently.
+  \end{itemize}
+
+  \noindent We remapped the state sequence based on the cluster assignments and
   generated a state transition probability matrix, $T$.
@@
 
-  We obtained $\mathbf{c}$ vectors of the clustered states by averaging 
-  each value of $\mathbf{c}$ assigned to the same cluster.
-  \begin{itemize}
-   \item We only care about the $r$ component of $\mathbf{c}$ because solute
-   trajectories are not bound in the $z$ direction.
-  \end{itemize}
+%  We obtained $\mathbf{c}$ vectors of the clustered states by averaging 
+%  each value of $\mathbf{c}$ assigned to the same cluster.
+%  \begin{itemize}
+%   \item We only care about the $r$ component of $\mathbf{c}$ because solute
+%   trajectories are not bound in the $z$ direction.
+%  \end{itemize}
 
   We used the parameter inference component of the IHMM algorithm in order to 
-  infer $A$ and $\Sigma$ of the clustered states.
+  infer $A$, $\Sigma$ and $\mu_r$ of the clustered states.
   \begin{itemize}
@@
    \item We did this by subtracting the maximum likelihood estimate
-   of the $\mathbf{c}$ vector from each same-state segement of the unclustered
+   of the $\mathbf{c}$ vector from each same-state segment of the unclustered
    trajectory.   
@@
 
-  Finally, we generated stochastic trajectory realizations using the clustered
+  \noindent Finally, we generated stochastic trajectory realizations using the clustered
   parameter sets.
@@
     occurred.
+  \end{itemize}
+
+  % BJC5: not sure what to title this. Or break it into more sections.
+  \subsection{Calculation of Physical Interactions}\label{method:interactions}
+
+  We determined the number of hydrogen bonds between each solute and the membrane
+  as a function of time.
+  \begin{itemize}
+    \item Based on the geometric criteria of Luzar and Chandler, we define a hydrogen
+    bond to exist if the distance between donor, D, and acceptor, A, atoms is less 
+    than 3.5\AA~and the angle formed by $D-H \cdots A$ is less than 30
+    $\degree$.~\cite{luzar_effect_1996}
+  \end{itemize}
+
+  We estimated the lifetime of hydrogen bonds by recording the length of 
+  sequential frames where solute remained hydrogen bonded.
+  \begin{itemize}
+    \item We still counted sequences where hydrogen bonds were broken for
+    a single frame before reforming.
+    \item We reported the 95th percentile of hydrogen bond lifetimes.
+  \end{itemize}
+
+  We also measured the degree of association between solutes and sodium ions on a
+  frame-by-frame basis.
+  \begin{itemize}
+    \item We define a sodium ion to be associated with an atom if they are within 
+    2.5 \AA~of each other, as determined in our previous work.~\cite{coscia_chemically_2019}
+  \end{itemize}
+
+  We developed a way to measure the local density of the membrane at arbitrary
+  points in the unit cell.
+  \begin{itemize}
+    \item We histogrammed the positions in three dimensions
+    \item Since our system is in a monoclinic unit cell, we periodically replicated
+    the system in +/- x, y and z direction and then set the bounds on the
+    histogram to create a rectanglular box encompassing the unitcell with a 1 nm
+    buffer between the histogram unitcell boundaries.
+    \item We then used a regular grid interpolator in order to allow interpolation
+    at arbitray points within the grid.
+  \end{itemize}
+
+  We quantified average solute movement using the time averaged mean squared 
+  displacment (MSD) of the solute center of mass trajectories.
+  \begin{itemize}
+
+ 	\item The time-averaged MSD measures all observed displacements over time lag $\tau$:
+  	\begin{equation}
+  	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
+  	\label{eqn:tamsd}
+  	\end{equation}
+  	where T is the length of the trajectory.
+  	\item We reported 1$\sigma$ confidence intervals based on the results of 200 
+  	bootstrap trials where calculated the mean of $n$ randomly chosen trajectories 
+  	with replacement from the pool of trajectories, where $n$ is the number of trajectories.
   \end{itemize}
@@
   	distinguishing these behaviors.   	
-  	\item The following approach to analysis demonstrates how one can break 
-  	down the very complex behavior exhibited by solutes over long MD trajectories 
-  	into discrete categories.
+  	\item The following approach to analysis demonstrates how one can discover and explain the very complex behavior exhibited by solutes over long MD trajectories 
+   in terms of solute-membrane interactions.
 %  	\item Clustering the behaviors helps us to tell a coherent story which
@@
     dynamics are most consistent, which implies that this particular methanol 
-    trajctory exhibits 8 distinct dynamical behaviors (in order of their first appearance,
+    trajectory exhibits 8 distinct dynamical behaviors (in order of their first appearance,
     they are colored dark yellow, red, light blue, light green, orange, blue, teal and lime green). 
@@
     state changes during that time period and red slivers in the bar above.
-    \item Signficant hops in the $z$ direction appear to be described by the blue
+    \item Signficant hops in the $z$ direction appear to be described by the dark blue
     state.
-    \item After entering the blue state ca. 850 ns, methanol appears to jump
+    \item After entering the dark blue state ca. 850 ns, methanol appears to jump
     signficantly in the $z$ direction from a hydrogen bonded state with the ether 
@@
 
-  \noindent It is clear that there is a wealth of information in these plots. 
+  \noindent It is clear that there is a wealth of information in these plots, but they don't give the complete picture needed in order to formulate LLC membrane design principles.
   \begin{itemize}
@@
     the traejectory with software like VMD.
-    \item However, a more general understanding of methanol's average behavior
-    is necessary in order to formulate LLC membrane design principles.
+    \item However, it is still possible to gain a more general understanding of methanol's average behavior.
   \end{itemize}
@@
     \item Of those, only six states appear in a third (8 out of 24) or more methanol 
-    trajectories, and 3 of them appear in over 50 \% of the methanol trajectories.
+    trajectories, and three of them appear in over 50 \% of the methanol trajectories.
     \item 12 of the detected states are shared by two or less methanol trajectories.  % 23 in 3 or less -- not sure which is better to say
     \item In Figure~\ref{fig:common_states_MET_lines}, we plot representative dynamics
-    of each of the six states which we determined to be prevelant.
+    of each of the six states which we determined to be prevalent.
     \item We also chose to study a seventh state, which only appears in three out of
@@
     \item Covariance in each dimension appears to have a strong correlation.
-    \item States 3 and 5 as well as states 4, 6 and 7 are primarily distinguished based
+    \item States 3 and 5 (in the pore region) as well as states 4, 6 and 7 (in the tail region) are primarily distinguished based
     on their autoregressive coefficients, A. 
@@
       less obstruction to solute motion.
-      \item It's dwell time of ca. 8 ns, suggests that solutes stay in this highly
-      mobile state for long enough to displace signficantly.
+      \item It's dwell time of ca.~8 ns, suggests that solutes stay in this highly
+      mobile state for long enough for their positions to displace signficantly.
   \end{itemize}
@@
   of the states using 1000 simulations of a Bernoulli process where we continued to draw until transitioning
-  out of the state with probability 1 - p. Of the prevelent states, states 1 and 
-  2 exhbit the shortest dwell times alongside their high covariances. States 3 and 6 have the longest dwell
-  times where methanol appears to be trapped near the pore center.   
+  out of the state with probability 1 - p. Of the prevalent states, states 1 and 
+  2 exhbit the shortest dwell times alongside their high covariances. States 5 and 7 have the longest dwell times in the pore and tail regions respectively.
   }\label{fig:common_states_MET}
@@
 
-  Our speculation so far is based purely on the parameters of our model compared to 
-  a single methanol trajectory.
+  Most of what we have learned thus far has been based on the parameters of our
+  model with some qualitative validation using a single methanol trajectory.
   \begin{itemize}
@@
 
-  The types of hydrogen bonding undergone by solutes is dependent on radial
-  location (see Figure~\ref{fig:hbond_pi_chart}).
+  \noindent The types of hydrogen bonding undergone by solutes is dependent on radial
+  location (see Figure~\ref{fig:hbond_pichart}).
   \begin{itemize}
@@
     to hydrogen bond with the monomer tails.
-    \item In the past we've shown how there is a gradual transition from the
+    \item In the past we've shown that there is a gradual transition from the
   	hydrophilic to hydrophobic region in these membranes, meaning the monomer
@@
 
-  States which exhibit longer dwell times have longer hydrogen bond lifetimes.
+  \noindent States which exhibit longer dwell times have longer hydrogen bond lifetimes (see
+  Figure~\ref{fig:hbond_pichart}).
   \begin{itemize}
@@
     their dwell times.
-    \item However, in the pores, this is not necessarily a linear relationship. 
-    \item For example, state 5 has the lowest hydrogen bond lifetime of states 3--6
+    \item However, in the pores, the same linear relationship does not hold.
+    \item For example, state 5 has the lowest hydrogen bond lifetime of states 3--7
     despite having the second longest dwell times. 
@@
 
-  The local density experienced by solutes may have an impact on the length of solute 
+  \noindent The local density experienced by solutes may have an impact on the length of solute 
   entrapment.
   \begin{itemize}
-    \item On average, solutes in state 5 are surrounded by an above average number of
-    particles. 
+    \item On average, solutes in state 5 are surrounded by a relatively high density
+    of particles.
     \item Based on its radial location and preference towards hydrogen bonding
-    with the ether linkages, it is reasonable to assume that while in state 5, methanol
-    spends most of its time just outside the pore region, sandwiched between the 
-    monomer head groups. 
+    with the ether linkages (see Figure~\ref{fig:hbond_pi_charts}), it is 
+    reasonable to assume that while in state 5, methanol spends most of its time just
+    outside the pore region, sandwiched between the monomer head groups. 
     \item Although state 5 hydrogen bonds break more frequently than one might expect for 
@@
 
-  States describing behavior in the tail region show a direction relationship between 
+  States describing behavior in the tail region show a direct relationship between 
   hydrogen bond lifetimes and local density.
   \begin{itemize}
-    \item Methanol molecules which experience state 2 are in a low density region of the
-    tails where they can easily break free of hydrogen bonds.
-    \item Methanol molecules in states 4 and 6 have hydrogen bond lifetimes that are similar
-    to the mean dwell times, which suggests
-    \item Finally, methanol molecules trapped in state 7 are in the densest region of all
+    \item Methanol molecules which experience state 2 spend their time in a low density 
+    region of the tails where they can easily break free of hydrogen bonds.
+%    \item Methanol molecules in states 4 and 6 experience intermediate-length dwell times.
+    \item Conversely, methanol molecules trapped in state 7 are in the densest region of all
     states studied. It is likely difficult for methanol to esacpe these high density regions
@@
 
-  %BJC3: I'm struggling a bit with this part of the analysis. The story isn't as clear
-  % cut as I want because it seems like states which contribute to the same cluster behave
-  % the way they do for somewhat varied reasons. Hence the short paragraph after this one.
-  We can attempt to understand the behavior described in Figure~\ref{fig:common_states_MET}
-  further by relating them to their interactions with the membrane. 
-  \begin{itemize}
-    \item It is clear that solutes can behave similar in different regions of the 
-    membrane because each state hydrogen bonds with LLC atoms located from the monomer head
-    groups to the tails. 
-    %BJC3: The following is a hypothesis to be tested.
-    \item The key difference is the lifetime of these interactions. 
-    \item When in a trapped state (one with smaller covariance like 2 and 4), hydrogen bond
-    lifetimes are generally longer.
-    \item While hydrogen bonds occur in states 1 and 3, the lifetimes are shorter, perhaps
-    broken by fluctuations in their local environment.
-  \end{itemize}
-
-  It is important to understand that the clustered parameter sets are
-  %MRS5: summaries-> averages?
-  essentially summaries of many related behaviors. Therefore, the most thorough
-  %MRS5->Figure 6 does have show that there is variance between trajectories. 
-  understanding of a specific segment will be gained using descriptive visualizations
-  like Figure~\ref{fig:mechanism_map}. But this model very clearly tells the user where
-  to look.
-  %BJC3: could do a case study of sorts on a chosen segment
-
-  %BJC3: this figure is not even close to done
-  %BJC3: I've tried a couple different things to look at the hbonds. The other was 
-  % how often they are hydrogen bonded in general versus not hydrogen bond. They all
-  % hydrogen bond about the same amount. So I think hbond lifetimes may be the key. 
-  % I need to implement this first to test that hypothesis.
-  %BJC4: I didn't put sodium ion assocaition in this because it's infrequent. 
-  %MRS5: is it correlated with specific states?
+  %BJC4: I didn't put sodium ion assocaition in this figure because it's infrequent. 
   %BJC4: If I compare to acetic acid or urea, I could add it back. I was thinking of splitting
@@
   \end{subfigure}
-  \caption{With our clustering approach, methanol exhibits similar state behaviors
-  %MRS5: So this is a little counterintuitive, in that the separate states have similar behavior.
-  %MRS5: Are there charts that show what is _different_ about the states as well?  The previous figure
-  %      Shows that they are dynamically different, but this structural pie charge says the existance
-  %      of H-bonding is not the reason . . . 
-  in all regions of the membrane. In all of the common states described in 
-  Figure~\ref{fig:common_states_MET}, methanol, at some point, hydrogen bonds with 
-  each region of the LLC monomer to an appreciable degree. However, methanol frequently
-  is not hydrogen bonded at all.
-  %BJC4: hypothesis yet to be tested. Somehow, I'll incorporate lifetimes into this plot
-  %MRS4: lifetimes would be good!
-  We can learn more by looking at the hydrogen bond lifetime. In states 2 and 4, solutes
-  stay hydrogen bonded for longer periods of time.
-  %MRS5: OK, here is some physical insight - local density is what determines trapping.
-Emphasize the physical mechanisms (wat does and doesn't come out physically because of these analyses) like this more explicitly.
-  %MRS5: can you make other graphs like the H-bond graph? like histogram/pie chart of local density
-  %MRS5: as a function of state?  What about r as a function of state?  what other ways are there to show
-  %MRS5: the characteristics of the states?
-  These longer lifetimes exist because, when hydrogen bonded, the local density is higher, preventing the 
-  bond from breaking so easily. In states 1 and 3, hbonds are fleeting interactions because
-  the surrounding density is low, allowing solutes to move more freely.
+  \caption{(a) Methanol hydrogen bonds with different segements of the LLC monomer
+  dependent on the state. States with mean radial locations in the pore region tend to
+  hydrogen bond with the head groups and ether linkages. States with mean radial
+  locations in the tails tend to hydrogen bond with the tail oxygen atoms.
+  (b) Hydrogen bond lifetimes and the local density experienced by methanol
+  molecules can help us to understand dynamical states in terms of membrane 
+  interactions. States 1 and 2, which have large covariances, also have short
+  hydrogen bond lifetimes and exist in relatively low density regions. The
+  hydrogen bond lifetimes of methanol in states with radial means in the tail
+  region tend to increase with local density and mean dwell times. This monotonic
+  relationship does not exist for states in the pore region. The high 
+  local density experienced by state 5 methanol molecules may explain why 
+  hydrogen bond lifetimes are short but dwell times are high. State 5 methanol's
+  preference towards hydrogen bonds with ether linkages suggests that the solute
+  sits between LLC monomer head group which prevent it from wandering to far
+  before recovering its previous hydrogen bond.
   }\label{fig:hbond_pichart}
@@
 
+  % BJC5: I think I want to do an abbreviated study here on acetic acid or urea 
+  % since it will incorporate sodium ion association.
+
   \subsection{Reproducing MD Trajectories and MSDs with the IHMM}
 
+  %BJC5: something we can do for the supporting information to show that this approach is valid: Eliminate nonidealities in our MD trajectories (compared to a pure VAR process) and use toy data to generate trajectories based on some number of states with different parameters.
+Generate an MSD with those.
+See if we can reproduce with our model.
+Can also use this to test new strategies.
+
   We can use the IHMM in order to generate stochastic trajectory realizations
-  which bear qualitatively similar characteristics to those output
+  which bear some qualitatively similar characteristics to those output
   by our MD simulations.
@@
     shared by the 24 MD trajectories.
-    \item Therefore, the realizations generated by our model are representative
-    of the average behavior of solutes studied.
     \item In Figure~\ref{fig:trajectory_realizations_MET}, we show some stochastic
@@
 
-  % BJC3: It might be good to show a few MD trajectories since they vary somewhat widely
-  % in behavior.
+  %BJC5: the goal is to figure out how to fix this for the paper.
+  %BJC5: this is more of a 'how can this be improved' section for the dissertation.
+  The MD trajectories show much broader variability in their overall motion than realizations
+  of the IHMM model. 
+  \begin{itemize}
+  		\item Some trajectories span a wide range of $z$ coordinates, while others stay
+  		trapped for nearly the entire simulation.
+  		\item Our model is very unlikely to generate trajectories with dwell times similar to 
+  		the third MD trajectory shown in Figure~\ref{fig:trajectory_realizations_MET}.
+        \item This is because the realizations generated by our model are representative
+        of the average behavior of solutes studied.
+        \item It is possible that certain states with long dwell times should have been
+        clustered as their own, but the transition probabilities would have high uncertainties.
+        \item It is also possible that we should not be using a static transition matrix in 
+        order to generate stochastic trajectories, but rather sample the rows of the transition
+        matrix from a Dirichlet distribution since average dwell times are highly sensitive to
+        self transition probabilities.
+  \end{itemize}
+  %BJC5: maybe a figure showing the MSDs of all the MD trajectories versus a subset of 
+  % stochastically generated trajectories. I image the stochastic ones will have a much
+  % tighter distribution.
+
   \begin{figure}
@@
   %MRS5: maybe it would be good to put a dotted line through each of the centers of the offset trajectories?
-  %MRS5: Do they really qualitatively reproduce?  the r behavior doesn't really look that similar, as it goes back
-  %      and forth, but not get stuck. 
-  %      Note: it's OK that if the model ends up not being able to describe the system, but we should be clear in 
-  %      what ways it does and doesn't.
-
-  \caption{We can qualitatively reproduce the average behavior of methanol trajectories
-  using our model. Solute trajectories generated by our model (blue) show the same
+  %BJC5: TODO 
+  \caption{We can generate trajectories which bear some qualitative resemblence to the MD 
+  trajectories. Solute trajectories generated by our model (blue) show the same
   hopping and trapping behavior exhibited by MD (black). The behavior of individual 
@@
   the model effectively represents the average behavior of the MD trajectories. This 
-  implies that much longer simulations might be necessary in order to obtain a set
-  of trajectories that explore state space to the same extent.
-  %BJC4: this observation is how I got the idea to calculate MSD by parameterizing
-  % individual trajectories  
-  %BJC4: Also note that I'm not currently happy with how I generate the radial dimension. 
-  %MRS5: how do you do that currently? We talked about generating dynamics in x, y, and z, 
-  %MRS5: (should be same parameters for x and y, because of symmetry), and then converting to r. 
-  %MRS5: could make this more clear in the methods. 
-  % Improvements will not affect z or the MSD because the VAR parameters won't change except for c
+  implies that much longer simulations or a different method of trajectory generation might
+  be necessary in order to obtain stochastic realizations with the same range of behavior
+  as MD.
    }\label{fig:trajectory_realizations_MET}
@@
     with uncharacteristically large MSDs.
+    \item It is possible that an improved trajectory generation approach may allow
+    for this highly variable behavior.
     \item If we remove these uncharacteristic trajectories, the agreement between 
     MD and our realizations improves. 
-    % BJC3: I'm not sure the best course of action. I've double checked the bootstrapping
-    % procedure and it make sense to me.
-    % MRS3: Thinking out loud - if 4/24 trajectories are big, then 
-    % (5/6)^24 = 0.013 will contain none of the 'big' trajectories.
-    % 24*(1/6)*(5/6)^23 = 0.060 will contain 1.
-    % C(24,2)*(1/6)^2*(5/6)^22 = 0.139 will contain 2
-    % C(24,3)*(1/6)^3*(5/6)^21 = 0.204 will contain 3 
-    % C(24,4)*(1/6)^4*(5/6)^20 = 0.214 will contain 4
-    % C(24,5)*(1/6)^5*(5/6)^19 = 0.171 will contain 5
-    % C(24,6)*(1/6)^6*(5/6)^18 = 0.108 will contain 6
-    % MRS5: so I guess it makes sense that the median bootstrap trajectory will have 4 big trajectories,
-    % MRS5: and that the 1 sigma line on the lower end will be ones with 2 'big' trajectories.
-    % MRS5: You could also plot the 95% confidence intervals
-    % BJC3: I could show how it's possible to get good agreeement with MD by only
-    % generating 24 solute trajectories since in some cases, outliers heavily weight the averages.
     \item Acetic acid has no obvious outliers and shows good agreement between MD and
@@
   % I think they should give the same results. Haven't tested it yet though. 
+  %BJC5: currently running these simulations then will write this section up.
 

### 2020-04-08 Ben_Manuscripts/hdphmm/Outline.tex
Some comments.

@@
   % BJC5: maybe even for the thesis
+  % MRS6: I agree on the details in SI, the thesis belongs in the paper. 
   \noindent The states identified by the IHMM are heavily influenced by the Gaussian prior
@@
    	mean levels are different.
+        %MRS6: should specify mean in both r and z if that's what you mean.
   \end{itemize}
@@
    	the squared differences within all clusters.
-   	\item We elected to choose the number of clusters rather than the distance
+        %MRS6: explain why Ward (make the cluster as minimally disperse?)
+   	\item We elected to choose the number of clusters rather than th distance
    	threshold.
@@
   % BJC5: not sure what to title this. Or break it into more sections.
+  % MRS6: ``exploring mechanism?''
   \subsection{Calculation of Physical Interactions}\label{method:interactions}
@@
     \item We reported the 95th percentile of hydrogen bond lifetimes.
+      %MRS6: why 95th percentile?
   \end{itemize}
@@
   \begin{itemize}  
-  	\item Our application of the IHMM does a good job of identifying and
+  	\item Our application of the IHMM does  good job of identifying and
   	distinguishing these behaviors.   	
+        %MRS6: will need to quantify ``good job''
   	\item The following approach to analysis demonstrates how one can discover and explain the very complex behavior exhibited by solutes over long MD trajectories 
@@
     \item Many of these modes are sampled very infrequently and thus do not merit significant study.
+      %MRS6: explain why don't merit additional study - should relate to how does not affect final results.
     \item In this section, we explore a subset of this data, focusing on the states
@@
 
+  %MRS6: likely just the summary of the methanol behavior should go in the main paper - the rest should be SI.
   \noindent Methanol exhbits a range of dynamic behavior.
@@
 
+  % MRS6: ideal for the paper would be summary infoormation about the 4 molecules, with more complete data from which the summary is drawn in SI.
   \subsection{Reproducing MD Trajectories and MSDs with the IHMM}
@@
 Can also use this to test new strategies.
-
+  %MRS6: toy data is actually a VERY good idea.  USe a VAR process that looks like MD, and then try to cluster it, and figure out why different.  
   We can use the IHMM in order to generate stochastic trajectory realizations
@@
   %BJC5: this is more of a 'how can this be improved' section for the dissertation.
+  %MRS6: got it.
   The MD trajectories show much broader variability in their overall motion than realizations
   of the IHMM model. 
+  %MRS6: definitely an important poiint for the paper: clustering things togethere might make trajectories too typical.
   \begin{itemize}
@@
         clustered as their own, but the transition probabilities would have high uncertainties.
+        %MRS6: is it necessarily a problem that the transition probabiblities have high uncertainties?
+If one is drawing from the Dirichlet distribution, uncertainy isn't a big deal.
+The trapping just doesn't quite seem to be as long as MD.
+        %MRS6: the other issue is apparent surpression on variance in the jumps, but that may be harder to get. 
         \item It is also possible that we should not be using a static transition matrix in 
@@
         self transition probabilities.
+        %MRS6: right uncertainty matters less here.
   \end{itemize}
@@
   %BJC5: currently running these simulations then will write this section up. 
+  %MRS6: it's possible that this section doesn't need to be in the paper, since it was describbed in the other one, and getting the selectivity isn't the main goal of this paper.
 

### 2020-04-09 Ben_Manuscripts/thesis/thesis.tex
Fleshing out outline
Updates to outline and minor changes to figures
Beginning of supporting info and figures. Draft updates, abstract for thesis

@@
 \usepackage{listings}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{booktabs}
+\usepackage{cleveref}
+\usepackage{booktabs}
+\usepackage{diagbox}
+\usepackage{array}
+
+\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
+\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
+\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
+\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
+\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
+\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
 
@@
 
-  % BJC: spliced together abstracts from papers with some additions
+  The ability to perform highly selective aqueous separations at low cost
+  is beneficial to a variety of chemical industries. Periodic, nanostructured 
+  porous polymer membranes made from the cross-linked inverted hexagonal phase
+  of self-assembled lyotropic liquid crystals (LLCs) are a promising class of 
+  materials for selective separations. In this thesis, we use atomistic molecular 
+  modeling in order investigate an experimentally characterized LLC polymer 
+  membrane.
 
-  The ability to perform highly selective aqueous separations at low cost
-  is beneficial to a variety of chemical industries
-
-  Periodic, nanostructured porous polymer membranes made from the cross-linked
-  inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
-  a promising class of materials for selective separations.
-
-  The uniform size and complex chemical topology of the pores formed by
-  self-assembled amphiphilic molecules such as liquid crystals make them
-  promising candidates for selective separations.
-
-  In this work, we investigate an experimentally characterized LLC polymer 
-  membrane using atomistic molecular modeling. We
-
-  First, we gained a deep understanding of nanoscopic pore structure in order 
-  to make sure we got the chemical environment in the pores correct.
-
-  In particular, we compare simulated X-ray
-  diffraction (XRD) patterns with experimental XRD data to quantify and
-  understand the differences between simulation and experiment.
-
-%  We find that the
-%  nanopores are likely composed of 5 columns of stacked LLC monomers which
-%  surround each hydrophilic core. Evidence suggests that these columns likely
-%  move independently of each other over longer time scales than accessible via
-%  atomistic simulation. We also find that WAXS structural features previously
-%  attributed to monomer tail tilt is likely instead due to ordered tail packing.
-%  Although this system has been reported as dry, we show that small amounts of
-%  water are necessary to reproduce all features from the experimental XRD pattern
-%  due to asymmetries introduced by hydrogen bonds between the monomer head groups
-%  and water molecules.
-
-  Finally, we explore the composition and structure of the
-  nanopores and reveal that there exists a composition gradient rather than an
-  abrupt partition between the hydrophilic and hydrophobic regions. A caveat is
-  that the time scales of the dynamics are extremely long for this system,
+  First, we gain a deep understanding of nanoscopic pore structure in order 
+  to make sure we can appropriately model the chemical environment in the pores.
+  In particular, we compare simulated X-ray diffraction (XRD) patterns with 
+  experimental XRD data to quantify and understand the major structural
+  features that we must incorporate into our model. We explore the composition 
+  and structure of the nanopores and reveal that there exists a composition gradient
+  rather than an abrupt partition between the hydrophilic and hydrophobic regions.
+  A caveat is that the time scales of the dynamics are extremely long for this system,
   resulting in simulated structures that appear too ordered, thus requiring
@@
 
-  %The clearer picture of the nanoscopic structure of these membranes
-  %provided in this study will enable a better understanding of the mechanisms of
-  %small molecule transport within these nanopores.
+  We use our carefully constructed molecular model in order to observe transport of
+  water, sodium ions and 20 small polar solutes within the pores of a lyotropic 
+  liquid crystal (LLC) membrane using atomistic molecular simulations. We find 
+  that the transport of a species is dependent not only on molecular size, but on
+  chemical functionality as well. We observe that all solutes perform intermittent 
+  hops between lengthy periods of entrapment. Three different trapping mechanisms 
+  are responsible for this behavior. First, solutes that drift out of the pore can
+  become entangled among the dense monomer tails. Second, solutes can donate 
+  hydrogen bonds to the monomer head groups. Third, solutes can coordinate with 
+  sodium counter ions. The degree to which a solute is affected by each mechanism 
+  is dependent on the chemical functionality of the solute.
 
-  We observe transport of water, sodium ions and 20 small polar
-  solutes within the pores of a lyotropic liquid crystal (LLC) membrane using
-  atomistic molecular simulations. We find that the transport of a species is
-  dependent not only on molecular size, but on chemical functionality as well.
-%  The membrane's inhomogeneous composition gives rise to radially dependent
-%  transport mechanisms with respect to the pore centers. 
-  We observe that all
-  solutes perform intermittent hops between lengthy periods of entrapment. Three
-  different trapping mechanisms are responsible for this behavior. First, solutes
-  that drift out of the pore can become entangled among the dense monomer tails.
-  Second, solutes can donate hydrogen bonds to the monomer head groups. Third,
-  solutes can coordinate with sodium counter ions. The degree to which a solute
-  is affected by each mechanism is dependent on the chemical functionality of the
-  solute.
-
-  %Using the insights developed in this study, we can begin to think about
-  %how to redesign existing LLC membranes in order to perform solute-specific
-  %separations.
-
-  Mathematically modeling complex transport phenomena at the molecular level
-  can be a powerful tool for identifying transport mechanisms and predicting
-  macroscopic properties. We use two different stochastic time series models,
-  parameterized from long molecular dynamics (MD) simulation trajectories of
-  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC)
-  membrane, in order to predict solute mean squared displacements (MSDs)
-  and solute flux, and thus solute selectivity, in macroscopic length pores.
+  The remainder of this thesis focuses on developing stochastic models meant to 
+  generate realizations of solute trajectories with similar qualitative and
+  quantitative dynamics to our MD trajectories solute trajectories. Mathematically 
+  modeling complex transport phenomena at the molecular level can be a powerful tool
+  for connecting microscopic chemically-dependent solute motions that do not
+  follow simple diffusive behavior with macroscopic membrane performances. 
+  We develop three different stochastic time series models, parameterized by long 
+  molecular dynamics (MD) simulation trajectories.
 
@@
   modeled as a fractional diffusion process subordinate to a continuous time
-  random walk. From the MD simulations, we parameterize the distribution of
-  dwell times, hop lengths between dwells and correlation between hops. We
-  explore two variations of the anomalous diffusion modeling approach. The first variation
-  applies a single set of parameters to the solute displacements and the second
-  applies two sets of parameters based on the solute's radial distance from the
-  closest pore center.
+  random walk. From our MD simulations, we parameterize the distribution of
+  dwell times, hop lengths between dwells and correlation between hops.
 
-  Next, we generalize Markov state models, treating the
-  configurational states of the system as a Markov process where each
-  state has distinct transport properties. For each state and transition
-  between states, we parameterize the distribution and temporal correlation
-  structure of positional fluctuations as a means of characterization and to
-  allow us to predict solute MSDs. We show that both models reasonably reproduce
-  the MSDs calculated from MD simulations. However, qualitative differences
-  between MD and Markov state dependent model-generated trajectories may limit
-  its usefulness.
+  Next, we generalize Markov state models, treating the configurational states of 
+  the system as a Markov process where each state has distinct transport properties. 
+  For each state and transition between states, we parameterize the distribution 
+  and temporal correlation structure of positional fluctuations as a means of 
+  characterization and to allow us to predict solute MSDs.
 
-  Finally, we demonstrate how one can use these models to
-  estimate flux of a solute across a macroscopic-length pore and, based on
-  those quantities, the membrane's selectivity towards each solute. This work
-  helps to connect microscopic chemically-dependent solute motions that do not
-  follow simple diffusive behavior with macroscopic membrane performance.
-
+  Building on what we learned from the first two models, we develop a third approach,
+  called the infinite hidden Markov model, which is capable of automatically 
+  distinguishing an unknown number of hidden dynamical modes in multidimensional
+  solute time series. This model offers a flexibile approach to modeling solute
+  motion and helps us to uncover mechanisms with minimal human effort.
   }
@@
   techniques to solute time series.
-
-  % BJC: should I mention the start-up? If so, I'm not sure what to say for that.
-  I would like to acknowledge my financial support: The ACS Petroleum Research Fund
-  grant \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN) 
-  fellowship which is funded by the U.S. Department of Education.
-
-  % BJC: This acknowledgement is how they want to be cited in papers. Could I
-  % shorten it for this?
-  Finally, I would like to acknowledge my high performance computing resources:
-  Molecular simulations were performed using the Extreme Science and
-  Engineering Discovery Environment (XSEDE), which is supported by National
-  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
-  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
-  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
-  which is supported by the National Science Foundation (awards ACI-1532235 and
-  ACI-1532236), the University of Colorado Boulder, and Colorado State
-  University. The Summit supercomputer is a joint effort of the University of
-  Colorado Boulder and Colorado State University.
+%  I would like to acknowledge my financial support: The ACS Petroleum Research Fund
+%  grant \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN) 
+%  fellowship which is funded by the U.S. Department of Education. 
+%
+%  % BJC: This acknowledgement is how they want to be cited in papers. Could I
+%  % shorten it for this?
+%  Finally, I would like to acknowledge my high performance computing resources:
+%  Molecular simulations were performed using the Extreme Science and
+%  Engineering Discovery Environment (XSEDE), which is supported by National
+%  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
+%  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
+%  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
+%  which is supported by the National Science Foundation (awards ACI-1532235 and
+%  ACI-1532236), the University of Colorado Boulder, and Colorado State
+%  University. The Summit supercomputer is a joint effort of the University of
+%  Colorado Boulder and Colorado State University.
 
@@
 
-\graphicspath{{../transport/figures/}{../structure_paper/figures/}{../transport/supporting_figures/}}
+\graphicspath{{../transport/figures/}{../structure_paper/figures/}{../transport/supporting_figures/}{../stochastic_transport/figures/}{../stochastic_transport/supporting_figures/}}
 
@@
 
-\input structure.tex
+%\input structure.tex
 %\input structure_si.tex
 
-\input transport.tex
+%\input transport.tex
 %\input transport_si.tex
+
+%\input stochastic_transport.tex
 
@@
 \appendix
-\input structure_si.tex
-\input transport_si.tex
+%\input structure_si.tex
+%\input transport_si.tex
+%\input stochastic_transport_si.tex
 

### 2020-04-10 Ben_Manuscripts/thesis/thesis.tex
Shortened abstract

@@
 
-  The ability to perform highly selective aqueous separations at low cost
-  is beneficial to a variety of chemical industries. Periodic, nanostructured 
-  porous polymer membranes made from the cross-linked inverted hexagonal phase
-  of self-assembled lyotropic liquid crystals (LLCs) are a promising class of 
-  materials for selective separations. In this thesis, we use atomistic molecular 
-  modeling in order investigate an experimentally characterized LLC polymer 
-  membrane.
+  Periodic, nanostructured porous polymer membranes made from the cross-linked
+  inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
+  a promising class of materials for selective separations. Our current understanding
+  of these systems is not sufficient to design them for specific applications. In 
+  this thesis, we use detailed atomistic molecular modeling in order to investigate 
+  structure and transport of solutes within LLC polymer membrane.
 
-  First, we gain a deep understanding of nanoscopic pore structure in order 
-  to make sure we can appropriately model the chemical environment in the pores.
-  In particular, we compare simulated X-ray diffraction (XRD) patterns with 
-  experimental XRD data to quantify and understand the major structural
-  features that we must incorporate into our model. We explore the composition 
-  and structure of the nanopores and reveal that there exists a composition gradient
-  rather than an abrupt partition between the hydrophilic and hydrophobic regions.
-  A caveat is that the time scales of the dynamics are extremely long for this system,
-  resulting in simulated structures that appear too ordered, thus requiring
-  careful examination of the metastable states observed in order to draw any
-  conclusions.
+  We begin by enhancing our understanding of the nanoscopic pore structure in order 
+  to ensure we appropriately model the chemical environment in the pores. We use radial
+  distribution functions and simulated X-ray diffraction patterns to quantify and 
+  understand the major structural features of the model.
 
@@
   water, sodium ions and 20 small polar solutes within the pores of a lyotropic 
-  liquid crystal (LLC) membrane using atomistic molecular simulations. We find 
-  that the transport of a species is dependent not only on molecular size, but on
-  chemical functionality as well. We observe that all solutes perform intermittent 
-  hops between lengthy periods of entrapment. Three different trapping mechanisms 
-  are responsible for this behavior. First, solutes that drift out of the pore can
-  become entangled among the dense monomer tails. Second, solutes can donate 
-  hydrogen bonds to the monomer head groups. Third, solutes can coordinate with 
-  sodium counter ions. The degree to which a solute is affected by each mechanism 
-  is dependent on the chemical functionality of the solute.
+  liquid crystal (LLC) membrane using atomistic molecular simulations. We 
+  observe that solutes perform intermittent hops between lengthy periods of 
+  entrapment and describe how transport of a species is dependent not only on 
+  molecular size, but on chemical functionality as well.
 
-  The remainder of this thesis focuses on developing stochastic models meant to 
-  generate realizations of solute trajectories with similar qualitative and
-  quantitative dynamics to our MD trajectories solute trajectories. Mathematically 
-  modeling complex transport phenomena at the molecular level can be a powerful tool
-  for connecting microscopic chemically-dependent solute motions that do not
-  follow simple diffusive behavior with macroscopic membrane performances. 
-  We develop three different stochastic time series models, parameterized by long 
-  molecular dynamics (MD) simulation trajectories.
+  Based on our qualitative understanding of solute transport, we focus the remainder
+  of our efforts on the development of three different stochastic models which can be
+  used to generate realizations of solute trajectories with qualitative and quantitative 
+  dynamics similar to our MD solute trajectories. Mathematically modeling complex 
+  transport phenomena at the molecular level can be a powerful tool for connecting 
+  microscopic chemically-dependent solute motions that do not follow simple diffusive
+  behavior with macroscopic membrane performance.
 
@@
   modeled as a fractional diffusion process subordinate to a continuous time
-  random walk. From our MD simulations, we parameterize the distribution of
-  dwell times, hop lengths between dwells and correlation between hops.
-
-  Next, we generalize Markov state models, treating the configurational states of 
-  the system as a Markov process where each state has distinct transport properties. 
-  For each state and transition between states, we parameterize the distribution 
-  and temporal correlation structure of positional fluctuations as a means of 
-  characterization and to allow us to predict solute MSDs.
-
-  Building on what we learned from the first two models, we develop a third approach,
+  random walk. We parameterize the distribution of dwell times, hop lengths between
+  dwells and correlation between hops. Next, we generalize Markov state models, treating
+  the configurational states of the system as a Markov process where each state has 
+  distinct transport properties. Finally we implement a third approach,
   called the infinite hidden Markov model, which is capable of automatically 

### 2020-04-10 Ben_Manuscripts/hdphmm/Draft.tex
Added draft tex

\documentclass{article}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{setspace}
\doublespacing

\externaldocument[S-]{Supporting_Information}

\title{Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
       of Solute Trajectories in Nanostructured Membranes.}

\author{Benjamin J. Coscia, Christopher P. Calderon, Michael R. Shirts}

\begin{document}

  \graphicspath{{./figures/}}
  \maketitle

  % BJC2: I'm not putting a lot of effort into the introduction since I'll only write
  % an abbreviated form for my dissertation. I'll work on the intro after my defense.

  \section{Introduction}

%  There is a need for highly selective membranes in order to perform efficient 
%  separations of components of complex aqueous streams.
%  %MRS2: add some more examples (When you get around to it).
%  \begin{itemize}
%    \item Organic micropollutants
%    \item Desalination and boric acid removal from seawater.
%    \item While many researchers focus on membrane permeability, we may be 
%    able to reduce costs of commercial nanofiltration and reverse osmosis with
%    higher selectivity.~\cite{werber_materials_2016}
%  \end{itemize}
%
%%  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.
%%  \begin{itemize}
%%    \item 
%%  \end{itemize}
%
%  Lyotropic liquid crystals (LLC) are a class of amphiphilic molecules whose ordered phases
%  can be cross-linked into mechanically strong membranes capable of highly selective
%  separations.
%  \begin{itemize}
%    \item The shape of the LLC monomers and water content dictates the ordered phase 
%    that they form. There are two phases of particular interest for membrane applications.
%  	\item H\textsubscript{II} phase lyotropic liquid crystals are characterized by 
%  	hexagonally packed, straight, pores while the Q\textsubscript{I} phase consists of
%  	a tortuous network of 3D interconnected pores. 
%  	\item In both cases the pores are uniform in size with radii on the order of 1 nm
%    %MRS2: is it really a molecular weight cutoff?
%    %BJC2: is molecular size better? Obviously there are other factors like shape, but I don't want to get into that
%  	giving them a very strict molecular size cut-off.
%	\item Additionally, they have the potential to disrupt conventional membrane separation
%	techniques by being selective based not only on size and charge, but on chemical
%	functionality as well.
%	\item Their pores are lined with LLC monomer functional groups which can potentially
%	be designed to interact with solutes in a chemically-specific manner
%  \end{itemize}
%
%  There are limits to what we can learn from experiment about LLC membrane design.
%  \begin{itemize}
%    \item Experimental observables like permeability and selectivity allow us to speculate
%    about the molecular origins of separation processes.
%    %MRS2: not quite sure what you mean below?
%    \item This drives an empirical design approach which can potentially neglect key
%    interactions which influence selectivity.
%    \item LLC membranes have been shown to exhibit selectivities which cannot be fully 
%    explained by relatively simple macroscopic models. 
%  \end{itemize}
%  
%  Molecular Dynamics (MD) simulations can give us mechanistic insights with atomistic 
%  resolution so that we can intelligently design new membranes for solute-specific 
%  separations.
%  \begin{itemize}
%    \item In our previous work, we built a detailed atomistic model which we used
%    to understand the nanoscopic structure of an LLC Membrane.~\cite{coscia_understanding_2019}
%    \item We also used the model in order to gain a qualitative understanding of 
%    trapping mechanisms which lead to subdiffusive transport behavior.~\cite{coscia_chemically_2019}
%  \end{itemize}
%
%  Unfortunately, the timescales that we can simulate with MD are insufficient to be
%  able to make well-converged predictions of macroscopic transport properties 
%  traditionally used to characterize membranes in the lab.
%  \begin{itemize}
%    %MRS2: would be good to get this next point into the first line of a paragraph, since it's quite important. 
%    \item However, if we use descriptive stochastic models that can capture solute
%    dynamics, then we could project long timescale behavior in addition to gaining
%    a deeper understanding of solute behavior on short timescales.
%  \end{itemize}

  %%%%%%%%%%%%%%%%%%%%%%%% Thesis chapter starts here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  In our previous work, we designed two different approaches which used
  solute time series in order to parameterize stochastic models that could be used
  to project transport on much longer timescales. In our first approach we modeled 
  solute trajectories as subordinated fractional Brownian and L\'evy motion, called
  the anomalous diffusion (AD) model. We generated solute trajectories by generating
  a series of anti-correlated hops separated by random periods of entrapment drawn 
  from a power law distribution. Our second approach treated solute motion as a Markov
  state model with state-dependent dynamics, called the Markov state-dependent dynamical
  model (MSDDM). We parameterized the state transition probabilities between
  each of eight discrete states as well as the solute dynamics within each of these
  states. We generated stochastic trajectory realizations by drawing a state
  sequence based on the transition probability matrix and incorporating the state dynamics
  while solutes were trapped in each state.

  Although both models had reasonable success at predicting solute mean squared 
  displacements (MSDs) on MD simulation timescales, they had shortcomings.
  The MSDDM failed to reproduce the hopping and trapping behavior that
  characterizes solute center-of-mass trajectories in our MD simulations.
  The AD model did not suffer this qualitative shortcoming, but the persistent 
  curvature of the predicted MSD curves suggested that the model might 
  underestimate MSDs on long timescales. The formulation of both models required
  careful examination and characterization of the interactions and dynamics exhibit
  by MD trajectories which required considerable human effort.

  In this work we attempt to minimize human effort by applying the infinite hidden 
  Markov Model (IHMM), a nonparameteric Bayesian classification technique, in order to 
  automatically detect and infer the parameters of an unknown number of latent
  autoregressive (AR) modes present in solute center-of-mass time series trajectories.
  We aim to address two primary scientific questions with this work. First, we want
  to know if the IHMM algorithm can help researchers efficiently uncover underlying
  transport mechanisms which give rise to different solute dynamical behavior.
  Second, we want to evaluate the ability of our model to reproduce solute trajectories
  in a stochastic manner so that we can use it to predict macroscopic transport 
  properties which would otherwise require much longer MD simulations.

  We use the parameters of the states identified by the IHMM in order to infer 
  dominant solute-membrane interactions and transport mechanisms. We cluster similar 
  state parameters in order to reduce the state space and to understand which segments 
  of the solute trajectories exhibit similar behavior. We support our mechanistic 
  hypotheses via quantitative comparison to various physical membrane properties and
  solute-membrane interactions.

  Because independent solute trajectories generated by MD simulations share 
  similar state dynamics, we can use the IHMM to generate stochastic trajectory 
  realizations which sample from all behavior exhibited by MD. We verify that our
  stochastic realizations reproduce the expected hopping and trapping behavior 
  exhibited by MD. We quantitatively validate these trajectories by comparing 
  their mean squared displacement (MSD) to MSDs measured by MD.

  \section{Methods}

  We ran all MD simulations and energy minimizations using GROMACS 2018. Our 
  python implementation of the IHMM algorithm is available online at 
  \texttt{https://github.com/bencoscia/hdphmm}. All other post-simulation 
  trajectory analysis tools are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.

  \subsection{Molecular Dynamics Simulations}

  We studied transport of solutes in the H\textsubscript{II} phase using an
  atomistic molecular model of four pores in a monoclinic unit cell with 
  10 \% water by weight. Approximately one third of the water molecules 
  occupy the tail region with the rest near the pore center.

  We chose to study a subset of 4 of the fastest moving solutes from our previous
  work: methanol, acetic acid, urea and ethylene glycol. In addition to exploring
  membrane structural space the most, these solutes have a relatively diverse set
  of chemical functionality. For each solute we created a separate system and to 
  each system we added 6 solutes per pore for a total of 24 solutes. This number 
  of solutes per pore provides a balance of a low degree of interaction between 
  solutes and a sufficient amount of data from which to generate statistics on the
  time scales which we simulate. Further details on the setup and equilibration of
  these systems are detailed in our previous work.\cite{coscia_chemically_2019}

  We let each solute undergo 5 $\mu$s of MD simulation. We used a time step of 2 fs
  at a pressure of 1 bar and temperature of 300K controlled by the Parinello-Rahman 
  barostat and v-rescale thermostat respectively. We recorded frames every 0.5 ns.

  \subsection{The Infinite State Hidden Markov Model}\label{method:IHMM}

  Hidden Markov models (HMMs) are a useful and widely used technique for modeling
  sequences of observations where the probability of the next observation in a 
  sequence depends, at least in part, on a previous unobserved, latent or hidden,
  state.~\cite{beal_infinite_2002} In the context of our simulations, the observations
  correspond to the center of mass coordinates of the solutes versus time, and the
  states correspond to the dynamical behavior which give rise to those types
  of observations. The probability of transitioning to a state based on the current
  state is mathematically defined in terms of an $n\times n$ transition probability
  matrix, $T$, where $n$ is the number of states. Unfortunately, standard HMMs 
  require $n$ to be known \textit{a priori}. One can partially overcome this by 
  testing a range of numbers of hidden states and determining which is the best 
  representation of the data.

  %BJC: I'm not sure how much of this I should include. This is pretty much 
  % a reproduction of Fox et al's explanation: https://ieeexplore.ieee.org/abstract/document/5563110
  The infinite-state HMM overcomes this drawback by placing a hierarchical
  Dirichlet process (HDP) prior on the transition probabilities. Using some 
  base probability distribution, $H$, a Dirichlet process (DP) generates discrete 
  distributions, $G_0$, over a countably infinite number of probability measures:
  \begin{equation}
      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
  \end{equation}
  where the $\theta_k$ are values drawn from the base distribution and the weights
  $\beta_k$ come from a stick-breaking process parameterized by the concentration 
  parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). In shorthand, this
  specification can be expressed as $G_0 \sim DP(\gamma, H)$. The concentration 
  parameter, $\gamma$, expresses one's confidence in the base distribution $H$.
  We use a uniform base distribution for $H$. When $\gamma\to 0$, the first 
  weight of $G_0$, $\beta_1$, approaches unity and for $\gamma\to\infty$, the weights
  become uniform and $G_0$ closely resembles $H$. Each row, $G_j$, of the transition 
  matrix is produced by drawing from a DP specified using the $\beta$ vector as a 
  discrete base distribution and a separate concentration parameter, $\alpha$.
  \begin{equation}
      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
  \end{equation}
  This hierarchical specification ensures that the transition probabilities in 
  each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
  Once the model has converged only a finite number of states will have significant
  sampling.

  We describe the dynamics of each state visited by solutes using a first order vector 
  autoregressive (VAR(1)) model. In general, a VAR($r$) process is characterized by a
  vector of observations in a time series that are linearly dependent on $r$ previous
  values of the time series vector:
  \begin{equation}
  	\mathbf{y}_t = \mathbf{c} + \sum_{i=1}^r A_i\mathbf{y}_{t-i} + \mathbf{e}_t~~~~\mathbf{e}_t \sim \mathcal{N}(0, \Sigma)
  \label{eqn:var}
  \end{equation}
  Previous observations are weighted by coefficient matrices, $A_i$. The VAR($r$) 
  process is further characterized by a shift in the mean of each dimension by the
  vector $\mathbf{c}$ and a white noise term $\mathbf{e}_t$.~\cite{hamilton_time_1994}
  We assumed $\mathbf{e}_t$ to be multivariate Gaussian noise, with mean zero and
  covariance, $\Sigma$. We limited our analysis to an autoregressive order of $r=1$.
  This means that we only parameterize $A_1$. To simplify notation, we will just
  call it $A$. We used a matrix-normal inverse-Wishart prior on parameters $A$ and 
  $\Sigma$ and a Gaussian prior on $\mathbf{c}$ in order to infer their 
  values.~\cite{fox_nonparametric_2009}

  % BJC2: It might be useful to walk through the following procedure with an example 
  % trajectory
  % TODO in the SI

  %Based on the algorithms developed by Fox et al.~\cite{fox_sticky_2007}, 
  Using the IHMM framework, we estimated the most likely number and sequence of hidden
  states in each solute center-of-mass trajectory while simultaneously inferring VAR(1)
  parameters for each state and the overall state transition probability matrix, $T$.
  We created a python implementation of this process which we heavily adapted from
  the MATLAB code of Fox et al.~\cite{fox_sticky_2007} Parameter estimation is iterative. 
  Therefore, we looked for convergence of each entry in the $\mathbf{c}$ vector as well
  as the $A$ and $\Sigma$ matrices of Equation~\ref{eqn:var}. We detected equilibration 
  of the parameters using the module \texttt{pymbar.timeseries.detect\_equilibration} on
  the time series of parameter estimates. Plots illustrating parameter convergence are 
  available in Section~\ref{S-section:convergence} of the Supporting Information. We refer the interested reader to 
  much more extensive descriptions of the inference and sampling procedures used to 
  estimate the VAR(1) parameters and the state sequence. ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}

  We carefully applied the IHMM algorithm in a way which takes advantage of the
  system's cylindrical symmetry. There are a number of viable ways in which one 
  could choose to analyze these time series. We could use all 3 dimensions straight
  from the output trajectory. We could use just the $z$ dimensional coordinate 
  since we are primarily interested in through-plane membrane transport. Ultimately, 
  we chose to use a multi-step procedure that we believe adequately distinguishes 
  every type of distinct dynamical behavior exhibited by the solutes. The final
  parameterization of the model is in cylindrical coordinates since each pore is a
  cylinder where we expect solutes to exhibit radially symmetric dynamics. We 
  present a step-by-step demonstration of our procedure in Section~\ref{S-section:ihmm_procedure}
  of the Supporting Information.

  We start by applying the IHMM algorithm to the 3D solute center-of-mass coordinate 
  trajectories transformed relative to the closest pore center. We tracked the solute's
  motion along the pore axis with the center-of-mass $z$ coordinate. Using the nearest
  pore center as the origin, we represented the radial distance of each solute's 
  center-of-mass from the pore center in 2 dimensions, $x$ and $y$ 
  %(see Figure~\ref{fig:cartesian_cylinder}). 
  By working in cartesian coordinates, we avoid
  mathematical complexity introduced by cylindrical coordinates while estimating the 
  state sequence.

% BJC6: I don't think this figure is necessary
%  \begin{figure}
%  \centering
%  %MRS3: does this preserve the z-axis symmmetry? Is it just ensuring
%  %that you can't jump that far, or is it limitinig the values that
%  %the mean can take? Apologies if it's not clear to me yet.  I'm
%  %pretty sure it's just limiting the jump (since y_t = c + f(y_t-1)),
%  %but would be good to make that explicit - ``i.e. we need to make sure it doesn't jump too far'')
%  %BJC5: preserving z-axis symmetry isn't needed yet at this stage. I use the
%  % means in z in order to distinguish states (specifically estimating the c vector).
%  % I get the radial means this way. Then just ignore z later.
%  \includegraphics[width=0.2\textwidth]{cartesian_cylinder.pdf}
%  \caption{Using the nearest pore center as the origin, we represented the solute's
%  location along the pore axis in terms of the $z$ coordinates and their radial distance
%  from the pore centers in 2 dimensions, $x$ and $y$.}\label{fig:cartesian_cylinder}
%  \end{figure}

  We applied the IHMM to each of the 24 solute trajectories independently.
  Although the IHMM is capable of identifying an infinite number of states, 
  a Dirichlet Process tends to exhibit a ``rich get richer" effect, favoring
  a fewer number of states. By applying the algorithm to each trajectory 
  independently, we reduce the possibility of lumping together multiple 
  similar states which we would prefer to stay separated before clustering.
  Note that the states identified by the IHMM are heavily influenced by 
  the Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. 
  In Section~\ref{S-section:prior_guesses} of the Supporting Information we outline our method for 
  choosing reliable prior parameters. The entries of $A$ and $\Sigma$ do 
  not vary over a wide range, so the final parameters were relatively insensitive
  to their priors.

  We ran 2000 iterations of the IHMM procedure in order to arrive at converged 
  state sequences and parameters for each state. Most parameters converged 
  quickly (within 50-100 iterations) while others took up to 1000 iterations.
  %BJC6: still need to make these figures.
  We defined the finalized parameters of each state as the average of the 
  parameters from each iteration recorded after the equilibration time point.
  We found the equilibration time point of each component of the $\mathbf{c}$ 
  vector as well as $A$ and $\Sigma$ matrices, and then used the longest 
  equilibration time of all dimensions as the equilibration time point.
  Further details are available in Section~\ref{S-section:convergence} of
  the Supporting Information.

  We reparameterized the time series, preserving the state sequence, in terms
  of the radial and axial coordinates ($r$, $z$) because $x$ and $y$ aren't 
  meaningful alone due to the system's radial symmetry. We converted the $x$ and 
  $y$ center-of-mass coordinates to $r$. We fixed the state sequence from the 
  3D parmeterization and applied the inference component of the IHMM procedure
  to the cylindrical trajectories in order to estimate the VAR(1) parameters in
  terms of $r$ and $z$. Since we fixed the state sequence, and we are using conjugate
  priors, the VAR parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}). Therefore, we only ran 
  the inference procedure for 100 iterations. 
  %However, note that the uncertainty in their
  %estimates are a function of the number of data points used in their estimate.

  We clustered like parameter sets in order to reduce the state space to
  a more easily interpretable size. For each solute studied, we identified 200-325
  independent states, each with separate VAR(1) parameters. Many of these states
  exhibit very similar dynamical behavior except their mean levels in $r$ and $z$
  are different.

  We reduced the parameter space used agglomerative clustering, a hierarchical
  clustering approach which uses a linkage criteria in order to successively merge
  similar clusters until a desired intracluster distance threshold or number of
  clusters is reached. We used the Ward linkage criteria, which works to minimize 
  the sum of the squared differences within all clusters.
    %MRS6: explain why Ward (make the cluster as minimally disperse?)
   	%BJC6: I'll add some plots to the SI and then write a better justification for
	% the paper. This is lower priority in mind for the thesis.
  We elected to choose the number of clusters rather than the distance threshold.
  For our data, non-parameteric methods such as Bayesian Gaussian mixture models tend
  to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
  of the Supporting Information).

  We clustered based on the two diagonal entries of $A$ and $\Sigma$ as well as the
  radial means, $\mu_r$, for a total of 5 variables. One can choose alternative clustering
  features, such as the eigenvalues of the $A$ and $\Sigma$ matrices, but we chose their 
  diagonals because they can be easily translated to solute behavior. The diagonals of $A$
  describe the correlation between sequential hops while the diagonals of $\Sigma$ describe
  the size of the hops in each dimension. We assume that cross correlations in the parameters
  are negligible for clustering.

  We also chose to cluster the diagonals of each matrix and the radial means
  independently before combining the clusters to assign final state labels. If we divide
  the total states into $m$ clusters based on the diagonal entries of $A$, $n$ more clusters 
  based on the diagonal entries of $\Sigma$, and $k$ clusters based on $\mu_r$, then there
  are a total of $mnk$ possible cluster combinations. This allows slightly more flexibility
  in the total number of states compared to clustering on all five features at once, since 
  there can be up to, but not necessarily exactly, $mnk$ states.

  Choosing the number of clusters can be somewhat subjective so
  we attempted to add some structure to the selection process by following
  a set of qualitative and quantitative guidelines. We used the silhouette 
  test in order to score the quality of clustering as a function of the number 
  of clusters chosen. For our data, the silhouette test generally favors the 
  lowest number of clusters possible (see Section~\ref{S-section:nclusters} of
  the Supporting Information). However, choosing too few clusters tends to 
  result in inadequate distinguishment between visually obvious differences in 
  dynamic behavior. This results in finalized parameter sets that are averages of
  distinct behavior which presents further problems with the predictive modeling
  that we discuss later on. We aimed to maintain the highest silhouette score,
  and thus lowest number of clusters, possible while verifying that visually 
  distinct states stayed separated. Based on these guidelines, we decided to 
  group the $A$ and $\Sigma$ parameters into five clusters each and the radial
  means into three clusters. Of the 75 distinct states allowed by this formulation,
  the solutes in this study showed behavior from 32--36 distinct clusters. While
  this may seem like a high number of states, many are sampled infrequently.

  We remapped the state sequence based on the cluster assignments and generated a
  state transition probability matrix, $T$. The IHMM algorithm also produces an estimate
  of $T$, but since we fixed the state sequence, we decided to explicitly calculate $T$ 
  by counting the number of transitions between states compiled across all trajectories.

  We used the parameter inference component of the IHMM algorithm in order to 
  infer $A$ and $\Sigma$ of the clustered states.
   %BJC2: I'm unsure of the precise reasoning here.
  We could not simply take the mean of the clustered $A$ and $\mathbf{e}_t$ 
  parameters because it is not clear that this is a linear 
  operation for this problem. To circumvent this problem, we modified the ($r$,
  $z$) solute trajectories so that they had a mean of zero, leaving only the 
  fluctations. We did this by the mean of each same-state segment of the 
  unclustered trajectory. We used the IHMM algorithm on this modified trajectory
  to infer the clustered state parameters by fixing the clustered state sequence.

  We obtained $\mathbf{c}$ vectors of the clustered states by averaging 
  each value of $\mathbf{c}$ assigned to the same cluster. Note that we only care
  about the $r$ component of $\mathbf{c}$ because solute trajectories are not 
  bound in the $z$ direction.

  Finally, we generated stochastic trajectory realizations using the clustered
  parameter sets. We drew state sequences with transition probabilities given by
  $T$. While in a given state, we simulated motion according to the VAR(1)
  parameterization of that state. After each state transition, we reset the 
  unconditional mean of each state based on the particle's position immediately
  before the state transition occurred.

  \subsection{Tools for Exploring Mechanisms}\label{method:interactions}

  We determined the number of hydrogen bonds between each solute and the membrane
  as a function of time. Based on the geometric criteria of Luzar and Chandler, we 
  define a hydrogen bond to exist if the distance between donor, D, and acceptor, 
  A, atoms is less than 3.5\AA~and the angle formed by $D-H \cdots A$ is less than 
  30 $\degree$.~\cite{luzar_effect_1996}

  We estimated the lifetime of hydrogen bonds by recording the length of 
  sequential frames where solutes remained hydrogen bonded. We still counted sequences
  where hydrogen bonds were broken for a single frame before reforming. Consistent
  with our previous work, we reported the 95th percentile of hydrogen bond lifetimes
  since their distribution is not Gaussian and to emphasize longer trapping periods.

  We also measured the degree of association between solutes and sodium ions on a
  frame-by-frame basis. We define a sodium ion to be associated with an atom if they
  are within 2.5 \AA~of each other, as determined in our previous work.~\cite{coscia_chemically_2019}

  We developed a way to measure the local density of the membrane at arbitrary
  points in the unit cell. We histogrammed the positions in three dimensions
  Since our system is in a monoclinic unit cell, we periodically replicated
  the system in the +/- x, y and z directions and then chose the bounds on the
  histogram in order to create a rectanglular box encompassing the unitcell with
  a 1 nm buffer between the histogram and unit cell boundaries. We then used a regular
  grid interpolator in order to allow interpolation at arbitray points within the grid.

  We quantified solute motion using the time averaged mean squared displacment (MSD)
  of the solute center of mass trajectories. The time-averaged MSD measures all observed
  displacements over time lag $\tau$:
  \begin{equation}
  	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory. We reported 1$\sigma$ confidence intervals 
  based on the results of 200 bootstrap trials. For each trail, we calculated the mean of 
  $n$ random trajectories chosen with replacement from the pool of trajectories, where 
  $n$ is the number of trajectories.

  \section{Results and Discussion}

  Solutes in this system show a wide range of behavior influenced by the 
  heterogeneity of the membrane's nanostructure as well as the interactions 
  between monomer and solute chemical functionality. Our application of the 
  IHMM can identify and distinguish these behaviors. The following approach 
  to analysis demonstrates how one can discover and explain the very complex
  behavior exhibited by solutes over long MD trajectories in terms of 
  solute-membrane interactions. Further, we can use the IHMM in order to generate
  stochastic trajectories, with dynamics similar to MD, so that we can estimate 
  macroscopic transport properties.

  \subsection{Automatic Detection of Distinct Dynamical Modes}\label{section:find_modes}

  We applied the IHMM to all trajectories of each of the four solutes studied.
  Based on our choice of clustering, we identified over 30 distinct dynamical
  modes for each solute. Many of these modes are sampled very infrequently and thus
  do not contribute signficantly to a general understanding of solute transport behavior.
  In this section, we explore a subset of this data, focusing on the states
  and dominant interactions most common to solute trajectories.

  \subsubsection*{The Case of Methanol}

  %MRS6: likely just the summary of the methanol behavior should go in the main paper - the rest should be SI.
  Methanol exhbits a range of dynamic behavior. In Figure~\ref{fig:mechanism_map}, we
  plot a representative 2D methanol trajectory in cylindrical coordinates. The coordinates
  are colored according to the cluster with which methanol's dynamics are most consistent,
  which implies that this particular methanol trajectory exhibits 8 distinct dynamical 
  behaviors (in order of their first appearance, they are colored dark yellow, red, light
  blue, light green, orange, blue, teal and lime green). The solute timeseries are coupled
  with color coded bars which describe the solute's local environment and physical 
  interactions that it undergoes at that trajectory frame. From the top, they describe 
  whether the solute is associated with sodium, whether the solute is hydrogen bonding
  with the monomer as well as to what part of the monomer it is hydrogen bonding, and 
  finally, the local number density surrounding the solute.

  \begin{figure}
  \centering
  \begin{subfigure}{0.75\textwidth}
  \includegraphics[width=\textwidth]{mechanism_map.png}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.24\textwidth}
  \includegraphics[width=\textwidth]{monomer_oxygens.png}
  \caption{}
  \end{subfigure}
  \caption{(a) We can learn a significant amount of detail about solute motion by viewing 
  solute trajectories color-coded according to their clustered dynamical behavior alongside
  plots of the dominant molecular interactions and descriptions of the membrane's local 
  environment. In the plot above, we show the radial and axial coordinates of a single
  methanol molecule over the course of the equilibrated portion of its MD simulation.
  Disjoint segments of the same color imply the solute behaves similarly at different 
  points of the trajectory because their VAR parameters place them in the same cluster. 
  There are eight distinct dynamical modes exhibited by this trajectory. In order
  of their first appearance, they are colored dark yellow, red, light blue, light green,
  orange, blue, teal and lime green. On the top of the plot are bars which represent different
  physical interactions and the membrane's local environment as a function of time. The top 
  bar is colored green at time points where solutes are associated with sodium. Methanol 
  associates with sodium ions relatively infrequently. The next bar down is colored when hydrogen
  bonds exist. The colors match the enlarged oxygen atoms highlighted in (b). Blue slivers
  correspond to hydrogen bonds donated to the monomer's carboxylate head group. Green slivers
  corrrespond to  hydrogen bonds donated to the ether linkages between the head groups
  and tails. Red slivers correspond to hydrogen bonds donated to the oxygens on the ends
  of the monomer tails. Methanol exhibits significant hydrogen bonding with all parts of
  the monomer. Which part of the monomer methanol hydrogen bonds to is heavily correlated
  to the solute's $r$ coordinate. Finally, the bar with the blue gradient represents the local 
  membrane density based on the solute's ($r$, $z$) coordinate. Darker shades of blue
  correspond to higher membrane densities. The density appears to be higher when methanol
  motion is restricted (e.g. from 75 to 550 ns). It is relatively low in areas where methanol's
  position fluctuates significantly (e.g. from 550 to 700 ns). 
  }\label{fig:mechanism_map}
  \end{figure}

  One can gain useful chemical intuition just by studying plots like
  Figure~\ref{fig:mechanism_map}. It is clear that, for methanol, association 
  with sodium is a much rarer interaction than hydrogen bonding with the 
  LLC monomers. Methanol hydrogen bonds to all regions of the monomers dependent
  on its radial position. Its fluctuations tend to be smallest when hydrogen bonded
  or in areas of high local number density. For example, from approximately 75 to 
  525 ns, methanol appears to be trapped in a high density region of the tails.
  In the time that follows, it enters a region of relatively low density where 
  fluctuations are quite large. During this time period, there is intermittent, 
  short-lived hydrogen bonding with the oxygen atoms at the tail ends, as suggested
  by the frequent state changes during that time period and red slivers in the bar
  above. Signficant hops in the $z$ direction appear to be described by the dark blue
  state. After entering the dark blue state ca. 850 ns, methanol appears to jump
  signficantly in the $z$ direction from a hydrogen bonded state with the ether 
  linkages to a hydrogen bonded state with a head group in a monomer below it.

  It is clear that there is a wealth of information in these plots, but they don't give
  the complete picture needed in order to formulate LLC membrane design principles. One
  can analyze each segment sequentially and form a clear picture of this instance of 
  methanol's behavior without the need to visulize the traejectory with software like VMD.
  However, it is still possible to gain a more general understanding of methanol's average
  behavior.

  %BJC: I'm not sure whether to spell out the numbers or not. 'six state' versus '6 states'; 'eight out of 24' or '8 out of 24'
  % 'State one or State 1' 
  We may learn the most by studying the dynamical modes common to the majority of 
  the solute trajectories. Using the IHMM, we identified 33 total dynamical modes 
  exhibited by methanol. Of those, only six states appear in a third (8 out of 24) 
  or more methanol trajectories, and three of them appear in over 50 \% of the 
  methanol trajectories. 12 of the detected states are shared by two or less 
  methanol trajectories. In Figure~\ref{fig:common_states_MET_lines}, we plot 
  representative dynamics of each of the six states which we determined to be prevalent.
  We also chose to study a seventh state, which only appears in three out of
  24 trajectories, because methanol experiences very long periods of entrapment
  while in this state. Long trapping events, even if they are relatively rare, will
  have a significant influence on solute flux. No trajectory contains all seven states.
  However, the trajectory in Figure~\ref{fig:mechanism_map} exhibits all modes except
  states 6 and 7. The states in Figure~\ref{fig:common_states_MET} are colored to match
  states that also appear in Figure~\ref{fig:mechanism_map}.

  We can begin to dissect the dynamics of each state by studying their parameters.
  States 1, 3 and 5 have radial means near 1 nm or less (see y axis of $r$ direction 
  plot in Figure~\ref{fig:common_states_MET_lines}), which suggest that they occur
  close to the pore centers. States 2, 4, 6 and 7 occur well within the tail region
  of the membrane. States 1 and 2 have higher covariances in both the axial and radial
  directions compared to all other states. Covariance in each dimension appears to have
  a strong correlation. States 3 and 5 (in the pore region) as well as states 4, 6 and
  7 (in the tail region) are primarily distinguished based on their autoregressive 
  coefficients, A. Higher values of A generally lead to more wandering about the state
  mean. One could argue that the parameters of states 3--7 are actually very close which
  suggests that solutes might behave alike in topologically distinct regions of the 
  membrane.

  Despite some similarity in their VAR parameters, the length of time spent in states 
  3--7 appears to be dependent on the solute's radial location. Based on the 
  self-transition probabilities, we estimated the average time spent by each solute in
  each state (Figure~\ref{fig:dwell_times_MET}). States 3, 5 and 7 have long dwell times
  relative to the rest because they have high self-transition probabilities. Somewhat 
  surprisingly, both states 3 and 5 correspond to solutes located close to a pore center,
  where one might expect solute motion to be less restricted. Although solutes in states
  4 and 6 are in the viscous tail region, their dwell times are only intermediate. This
  could be due to imhomogeneity in the tail region which causes transitions between many
  different trapped states but with litle net effect on solute MSD. However, there are
  instances of states within the tail region with dwell times that exceed 100--200 ns,
  as shown by our inclusion of state 7. There are no other states with dwell times longer
  than state 5 in the pore region.

  States 1 and 2 exhibit the shortest dwell times of the states studied. This is 
  consistent with the trajectory in Figure~\ref{fig:mechanism_map}. State 2 is the 
  shortest lived state, appearing to bridge other tail region states. State 1 
  appears to represent a significant hopping state. It has a high covariance and
  occurs near the pore center, where there is less obstruction to solute motion.
  It's dwell time of ca.~8 ns, suggests that solutes stay in this highly mobile 
  state for long enough for their positions to displace signficantly.

  \begin{figure}
  \centering
  \begin{subfigure}{0.6\textwidth}
  \includegraphics[width=\textwidth]{common_states_MET.pdf}
  \caption{}\label{fig:common_states_MET_lines}
  \end{subfigure}
  \begin{subfigure}{0.35\textwidth}
  % BJC: I'll bootstrap some errorbars on this by drawing the transition probabilities 
  % from a dirichlet distribution.
  \includegraphics[width=\textwidth]{A_sigma_scatter_MET.pdf}
  \caption{}\label{fig:A_sigma_scatter_MET}
  \includegraphics[width=\textwidth]{dwell_times_MET.pdf}  %BJC5: maybe better as 95 % confidence rather than mean
  \caption{}\label{fig:dwell_times_MET}
  \end{subfigure}
  \caption{We can learn the most about methanol's behavior by studying the dynamics
  of the states common to many of the methanol trajectories. In (a), we show representative
  dynamics of six states that are common to more than one third of the solute trajectories. 
  The $y$-axis labels of the $r$ coordinate plot specify the radial mean of each clustered 
  state. The percentage of trajectories in which the states appear are labeled to the right of
  the $r$ plots. States 1--5 appear in the trajectory shown in Figure~\ref{fig:mechanism_map}
  and are colored to match for easy visual comparison. All time series have a mean of zero and are
  shifted to put the mean in line with the $y$-axis labels for the purpose of visualizing them. 
  (b) We can begin to understand the solute behaviors demonstrated in (a) by understanding their VAR 
  parameters. States 1 and 2 have higher covariances in both the axial and radial directions compared
  to all other states. This should lead to signficant solute displacement. Covariance in each dimension
  appears to have a strong correlation. States 3--6 all have relatively low covariances, which may
  be characteristic of trapped states. They are primarily distinguished based on the magnitude of their 
  autoregressive coefficients, A, and radial means. Higher values of A imply motion which wanders 
  more about the mean. States 1, 3 and 5 have radial means near 1 nm or less, which suggest that they
  occur close to the pore centers. States 2, 4 and 6 occur well within the tail region of the membrane.
  (c) Using the transition probabilities (p), we estimated the average time spent within each 
  of the states using 1000 simulations of a Bernoulli process where we continued to draw until transitioning
  out of the state with probability 1 - p. Of the prevalent states, states 1 and 
  2 exhbit the shortest dwell times alongside their high covariances. States 5 and 7 have the longest dwell times in the pore and tail regions respectively.
  }\label{fig:common_states_MET}
  \end{figure}

  Most of what we have learned thus far has been based on the parameters of our
  model with some qualitative validation using a single methanol trajectory. While 
  we may be able to further corroborate our arguments by analyzing more
  individual trajectories, it is more useful to correlate the state behavior with
  solute-membrane interactions.

  The types of hydrogen bonding undergone by solutes is dependent on radial
  location (see Figure~\ref{fig:hbond_pichart}). States with radial means near 1 nm
  or less (states 1, 3 and 5) typcially hydrogen bond with the monomer carboxylate
  groups and ether linkages. States with radial means greater than 1 nm (states 2,
  4, 6 and 7) tend to hydrogen bond with the monomer tails. In the past we've shown
  that there is a gradual transition from the hydrophilic to hydrophobic region in
  these membranes, meaning the monomer location is not tightly bound in $r$. Therefore,
  there are instances of hydrogen bond interactions that one might consider 
  uncharacteristic based on the state's radial mean.

  States which exhibit longer dwell times have longer hydrogen bond lifetimes (see
  Figure~\ref{fig:hbond_pichart}). States 3--7 have significantly longer hydrogen 
  bond lifetimes than states 1 and 2. It makes physical and mathematical sense that
  states 1 and 2 should not stay trapped by hydrogen bonding for long periods because
  they typically take large hops as communicated by their large covariances.
  In the tail states, hydrogen bond lifetimes appear to increase with their dwell 
  times. However, in the pores, the same linear relationship does not hold.
  For example, state 5 has the lowest hydrogen bond lifetime of states 3--7
  despite having the second longest dwell times.

  The local density experienced by solutes may have an impact on the length of solute 
  entrapment. On average, solutes in state 5 are surrounded by a relatively high density
  of particles. Based on its radial location and preference towards hydrogen bonding
  with the ether linkages (see Figure~\ref{fig:hbond_pi_charts}), it is reasonable to
  assume that while in state 5, methanol spends most of its time just outside the 
  pore region, sandwiched between the monomer head groups. Although state 5 hydrogen
  bonds break more frequently than one might expect for a state with long dwell times,
  it is possible that the solute's dense surroundings prevent it from wandering off 
  before the hydrogen bonding interaction can be recovered. This may explain the 
  behavior of the methanol in state 5 of the trajectory in Figure~\ref{fig:mechanism_map}
  where the solute's center of mass appears to move more freely about its mean than 
  other trapped states. The data suggests that methanol molecules in state 3 lie closer
  to the pore center than state 5 because they tend to hydrogen bond most frequently 
  with the carboxylate groups. Methanol molecules which experience state 3 are subject 
  to a lower density local environment and rely more heavily on hydrogen bonding interactions, 
  evidenced by their longer lifetimes, to stay trapped.

  States describing behavior in the tail region show a direct relationship between 
  hydrogen bond lifetimes and local density. Methanol molecules which experience state 2 
  spend their time in a low density region of the tails where they can easily break free
  of hydrogen bonds. Conversely, methanol molecules trapped in state 7 are in the densest 
  region of all states studied. It is likely difficult for methanol to esacpe these high 
  density regions and its position is further stabilized via hydrogen bonding.

  %BJC4: I didn't put sodium ion assocaition in this figure because it's infrequent. 
  %BJC4: If I compare to acetic acid or urea, I could add it back. I was thinking of splitting
  % the pi chart in half with slices corresponding to hbonds on one side and association on the other
  \begin{figure}
  \centering
  \begin{subfigure}{0.54\textwidth}
  \includegraphics[width=\textwidth]{hbond_pi_charts.pdf}
  \caption{}\label{fig:hbond_pi_charts}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hbond_lifetimes_density_MET.pdf}
  \caption{}\label{fig:hbond_lifetimes_density_MET}
  \end{subfigure}
  \caption{(a) Methanol hydrogen bonds with different segements of the LLC monomer
  dependent on the state. States with mean radial locations in the pore region tend to
  hydrogen bond with the head groups and ether linkages. States with mean radial
  locations in the tails tend to hydrogen bond with the tail oxygen atoms.
  (b) Hydrogen bond lifetimes and the local density experienced by methanol
  molecules can help us to understand dynamical states in terms of membrane 
  interactions. States 1 and 2, which have large covariances, also have short
  hydrogen bond lifetimes and exist in relatively low density regions. The
  hydrogen bond lifetimes of methanol in states with radial means in the tail
  region tend to increase with local density and mean dwell times. This monotonic
  relationship does not exist for states in the pore region. The high 
  local density experienced by state 5 methanol molecules may explain why 
  hydrogen bond lifetimes are short but dwell times are high. State 5 methanol's
  preference towards hydrogen bonds with ether linkages suggests that the solute
  sits between LLC monomer head group which prevent it from wandering to far
  before recovering its previous hydrogen bond.
  }\label{fig:hbond_pichart}
  \end{figure}

  % BJC5: I think I want to do an abbreviated study here on acetic acid or urea 
  % since it will incorporate sodium ion association.

  \subsubsection*{Behavior of Other Solutes}

  We applied the IHMM to the other three solutes in this study: urea, acetic acid
  and ethylene glycol. 
  \begin{itemize}  
    \item Not only can we use the model to study the dynamics of each solute 
    individually, but we can compare their behavior in order to improve our
    understanding of more subtle mechanistic details.
  \end{itemize}

  The size and chemical functionality of the solutes dictates the interactions which
  influence solute transport. 
  \begin{itemize}  
    \item In Figure~\ref{fig:hbonds_assoc_summary}, we show that the solutes 
    donate hydrogen bonds and associate with sodium ions to varying degrees.
    \item We also show the solute MSDs after a 1000 ns time lag. 
    \item It is not immediately obvious why the MSDs follow this trend.
    \item The states identified by the IHMM can help us shed some light.
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hbonds_assoc_summary.pdf}
  \caption{}\label{fig:hbonds_assoc_summary}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{rdf_summary.pdf}
  \caption{}\label{fig:rdf_summary}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{dwell_time_summary.pdf}
  \caption{}\label{fig:dwell_time_summary}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{cov_summary.pdf}
  \caption{}\label{fig:cov_summary}
  \end{subfigure}
  \caption{(a) Solutes hydrogen bond and associate with sodium ions
  to different degrees. Sometimes, they participate in both interactions at
  once. The frequency at which solutes interact via either mechanism does
  not appear to be linearly related to the solute's mean squared displacement
  after a 1000 ns time lag. (b) We histogrammed the means of the clusters weighted
  by the number of emissions from that cluster. Most solutes spend the majority of
  their time close to the pore center. Only methanol has a significant peak
  beyond 1.5 nm from the pore center. (c) The trend in the maximum dwell time
  among prevalent states for each solute is inversely related to the
  solute's MSD. In some cases, non-prevalent states show very long dwell times,
  which may have a significant impact on solute MSD. (d) All solutes tend to
  take larger hops in the $z$ direction when they are in the pore versus in 
  the tails. All solutes except urea make slightly larger radial hops while 
  in the tails.
  %BJC6: I made this plot out of curiosity, not sure if I'll use it yet.
  }\label{fig:summaries}
  \end{figure}

  Hydrogen bonding and sodium ion association interactions are far more 
  common when solutes stay near the pore centers.
  \begin{itemize}
    \item In Figure~\ref{fig:rdf_summary}, we plot the distribution of the 
    radial means of each cluster weighted by the time spent in that cluster.
    \item All solutes except methanol spend the majority of their time near
    the pore centers (roughly defined as within 1.5 nm).
    \item As we showed earlier, methanol spends a significant portion of its
    time trapped in the dense tails.
  \end{itemize}

  % BJC: we can probably use this to create a new definition of the pore and tail region.
  % and perhaps focus on transitions between them.
  Solute size likely has a large effect on their preferred radial location within
  the pores.
  \begin{itemize}
    \item The histograms in Figure~\ref{fig:rdf_summary} have a clear vacancy between
    what one might consider the pore and tail region, most evident in methanol's 
    distribution of radial positons.
    \item The area between the head groups and the distal regions of the tails is
    dense and hydrophobic which creates a considerable energy barrier to be overcome
    in order to transition to that region.
    %BJC: I wonder if there is a state which corresponds to the jump from pore to tail region. MIght be hard to pick up.
    \item Methanol is the smallest solute in this study and therefore appears to 
    have the easiest time crossing into the tails. 
  \end{itemize}

  Despite their close proximity to the low density aqueous pore region, acetic
  acid, ethylene glycol and urea exhibit a range of trapping behavior.
  \begin{itemize}
    \item It is clear that the number of polar interactions is not directly
    related to solute MSD. Acetic acid participates in a similar number of 
    interactions relative to urea and ethylene glycol, but its MSD is considerably
    lower.
    \item For the purpose of this analysis, as in the previous section, we 
    defined states that appear in more than one third of the trajectories to
    be prevalent states.
    \item In Figure~\ref{fig:dwell_time_summary}, we plot the longest dwell
    times exhibited by each solute among the prevalent states as well 
    as out of all the states.
    \item The state which exhibits the longest dwell times among all acetic
    acid states appears in 9 different trajectories, making it a prevalent state,
    and occurs 1 nm from the pore center. %BJC: check exact radius
    \item Although urea possesses the state with the longest dwell time among the
    solutes studied, it occurs in the tail region with prevelant states having 
    much shorter dwell times.  %BJC: get radius of long entrapment.
    \item Ethylene glycol appears to be the least subject to trapping.
  \end{itemize}

%  The combination of a carbonyl group, which binds strongly to sodium, and a 
%  hydroxyl group, which can form strong hydrogen bonds, makes acetic acid
%  particularly prone to trapping.
%  BJC6: more complicated than this. I will revisit.

  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}

  %BJC5: something we can do for the supporting information to show that this approach is valid: Eliminate nonidealities in our MD trajectories (compared to a pure VAR process) and use toy data to generate trajectories based on some number of states with different parameters. Generate an MSD with those. See if we can reproduce with our model. Can also use this to test new strategies.
  %MRS6: toy data is actually a VERY good idea.  USe a VAR process that looks like MD, and then try to cluster it, and figure out why different.

  We can use the IHMM in order to generate stochastic trajectory realizations
  which bear some qualitatively similar characteristics to those output
  by our MD simulations. Because we clustered the data, we are left with a 
  single transition probability matrix which allows transitions between dynamical
  behaviors shared by the 24 MD trajectories. In 
  Figure~\ref{fig:trajectory_realizations_MET}, we show some stochastic realizations
  generated by our models compared directly to MD. The trajectories show clear 
  periods of entrapment with intermittent hops.

  %BJC5: the goal is to figure out how to fix this for the paper.
  %BJC5: this is more of a 'how can this be improved' section for the dissertation.
  %MRS6: got it.
  The MD trajectories show much broader variability in their overall motion than realizations
  of the IHMM model. 
  %MRS6: definitely an important poiint for the paper: clustering things togethere might make trajectories too typical.
  Some trajectories span a wide range of $z$ coordinates, while others stay
  trapped for nearly the entire simulation. Our model is very unlikely to generate 
  trajectories with dwell times similar to the third MD trajectory shown in 
  Figure~\ref{fig:trajectory_realizations_MET}. This is because the realizations 
  generated by our model are representative of the average behavior of solutes studied.
  It is possible that certain states with long dwell times should have been
  clustered as their own, but the transition probabilities would have high uncertainties.
        %MRS6: is it necessarily a problem that the transition probabiblities have high uncertainties? If one is drawing from the Dirichlet distribution, uncertainy isn't a big deal. The trapping just doesn't quite seem to be as long as MD.
        %MRS6: the other issue is apparent surpression on variance in the jumps, but that may be harder to get. 
  It is also possible that we should not be using a static transition matrix in 
  order to generate stochastic trajectories, but rather sample the rows of the transition
  matrix from a Dirichlet distribution since average dwell times are highly sensitive to
  self transition probabilities.
        %MRS6: right uncertainty matters less here.
  %BJC5: maybe a figure showing the MSDs of all the MD trajectories versus a subset of 
  % stochastically generated trajectories. I image the stochastic ones will have a much
  % tighter distribution.

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{trajectory_realizations_MET.pdf}
  %MRS5: maybe it would be good to put a dotted line through each of the centers of the offset trajectories?
  %BJC5: TODO: redo these plots with r clusters
  \caption{We can generate trajectories which bear some qualitative resemblence to the MD 
  trajectories. Solute trajectories generated by our model (blue) show the same
  hopping and trapping behavior exhibited by MD (black). The behavior of individual 
  MD trajectories tend to show wider variability than our model's realization because
  the model effectively represents the average behavior of the MD trajectories. This 
  implies that much longer simulations or a different method of trajectory generation might
  be necessary in order to obtain stochastic realizations with the same range of behavior
  as MD.
   }\label{fig:trajectory_realizations_MET}
  \end{figure}

  The MSDs calculated by stochastic realizations of our model are quantitatively similar to
  MD. For all solutes except acetic acid, our predicted MSD curve lie close to but below the
  1$\sigma$ confidence intervals of MD. However, in these cases, the average MD MSDs are 
  driven up by single trajectories with uncharacteristically large MSDs. It is possible that
  an improved trajectory generation approach may allow for this highly variable behavior.
  If we remove these uncharacteristic trajectories, the agreement between MD and our realizations
  improves. Acetic acid has no obvious outliers and shows good agreement between MD and
  IHMM realizations.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_MET.pdf}
  \caption{}\label{fig:msd_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_GCL.pdf}
  \caption{}\label{fig:msd_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_URE.pdf}
  \caption{}\label{fig:msd_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_ACH.pdf}
  \caption{}\label{fig:msd_ACH}
  \end{subfigure}
  \caption{The MSDs predicted based on 1000 realizations of our model (blue) tend to underpredict
  the MSDs based on the MD trajectories (black). Due to the variability in solute behavior across MD trajectories,
  as demonstrated in Figure~\ref{fig:trajectory_realizations_MET}, there are several 
  individual solute MSD curves that are significantly higher than the rest and drive up the
  mean of the MSD. If we remove those trajectories from the MSD calculation, we obtain 
  estimates much closer to the IHMM estimate.(I haven't done it yet, but could plot a third curve
  with outlier removed). Acetic acid, has no obvious outliers which is consistent with our model's
  prediction which lies within the 1$\sigma$ confidence interval of MD after a 1000 ns time lag.}\label{fig:msds}
  \end{figure}

  % BJC3: maybe need to talk about the curvature. Our model shouldn't have noticeable
  % curvature because it's only correlated with one step

  \section{Conclusion}

  We have shown that the IHMM can be used to automatically parameterize solute 
  time series with an unknown number of latent dynamical modes. Initially, we applied
  the algorithm to each trajectory independently. For each solute studied, this resulted
  in over 300 distinct states. By clustering the parameter sets we were able to reduce 
  the state space to 10\% of its original size by grouping states with similar VAR
  parmeters.

  We coupled analysis of the clustered parameter sets with measurements of membrane 
  properties and solute-membrane interactions in order to gain a detailed understanding
  of the diverse sets behavior exhibited by solutes in these membranes. We showed how
  solute motion is influenced by hdyrogen bonding, sodium ion association and local
  membrane density. These interactions have a direct impact on the size and
  correlation of sequential solute steps.

  % BJC6: I'll weaken this for the thesis, but this is what I hope to say in the 
  % final paper.
  Finally, we show how one can generate stochastic realizations of our model that
  can qualitatively and quantitatively reproduce the behavior of MD solute 
  trajectories. The realizations show the hopping and trapping behavior that is
  characteristic of polar solutes in this system. We can also use them to reproduce
  the solute MSDs measured from the MD traejectories. The low computational expense 
  of generating these stochastic trajectories allows one to project solute behavior
  on much longer timescales and thus predict experimentally-relevant macroscopic 
  transport properties like solute flux and selectivity.

  We showcase this modeling approach by example, but it is important to
  recognize the generality of this analysis, especially in the context of molecular
  simulations. Vector autogregressive models can describe a diverse set of behavior
  and so the IHMM may be suited to study many types motion, including those not 
  characterized by hopping and trapping. The IHMM is a powerful approach for 
  understanding particle motion as well as for generating cheap models
  which can give macroscopic insight.

  \section*{Supporting Information}

  Detailed explanations and expansions upon the results and procedures mentioned in
  the main text are described in the Supporting Information. This information is
  available free of charge via the Internet at http://pubs.acs.org.

  \section*{Acknowledgements}

  %MRS2: add GAANN and PRF here to cover bases.
  This work was supported in part by the ACS Petroleum Research Fund
  grant \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN) 
  fellowship which is funded by the U.S. Department of Education. 
  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  \clearpage

  \bibliographystyle{ieeetr}
  \bibliography{hdphmm}

  %\newpage

  %\section*{TOC Graphic}

\end{document}

### 2020-04-10 Ben_Manuscripts/hdphmm/Supporting_Information.tex
added missing file

\documentclass{article}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}

\externaldocument[M-]{Draft}

\title{Supporting Information: Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
       of Solute Trajectories in Nanostructured Membranes.}

\author{Benjamin J. Coscia, Christopher P. Calderon \and Michael R. Shirts}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thetable}{S\arabic{table}}

\begin{document}

  \graphicspath{{./supporting_figures/}}
  \maketitle

  \section{Demonstration of IHMM Parameterization Procedure}\label{section:ihmm_procedure}

  Parameterization of trajectories by the IHMM is a multi-stepped procedure. In the figures
  that follow, we graphically illustrate the procedure which is described in detail in
  Section~\ref{M-method:IHMM} of the main text.

  \begin{enumerate}
  	\item Parameterize in $x$, $y$, $z$ coordinates with $x$, $y$ coordinates relative to the nearest
  	pore center (see Figure~\ref{fig:xyz_hmm}). 	
  	\item Convert x and y coordinates to radial coordinates, $r$, then fix the state sequence
  	and use the inference component of the IHMM in order to estimate the parameters in terms
  	of $r$ and $z$ (see Figure~\ref{fig:rz_hmm}). 	 	
  	\item Cluster the VAR parameters from the states found in all 24 trajectories. Reassign the state
  	sequence so that segments which belong to the same cluster are labeled the same across all solute
  	trajectories.
  	\item Subtract the mean of each segment, obtained before clustering, in order to zero out the
  	trajectory.
  	\item Fix clustered state sequence and infer parameters of each state, assuming a mean of zero
  	for all states (see Figure~\ref{fig:zeroed_hmm}). 
  \end{enumerate}

  \begin{figure}
    \centering
	\begin{subfigure}{0.8\textwidth}
		\includegraphics[width=\textwidth]{xyz_hmm.pdf}
		\caption{}\label{fig:xyz_hmm}
	\end{subfigure}  	
	\begin{subfigure}{0.8\textwidth}
		\includegraphics[width=\textwidth]{rz_hmm.pdf}
		\caption{}\label{fig:rz_hmm}
	\end{subfigure}  
	\begin{subfigure}{0.8\textwidth}
		\includegraphics[width=\textwidth]{zeroed_hmm.pdf}
		\caption{}\label{fig:zeroed_hmm}
	\end{subfigure}  
	\caption{IHMM parameterization is a multi-step procedure. In the above plots, distinct colors
	correspond to distinct state behavior. (a) First we parameterize the trajectories in terms of
	the $x$, $y$, $z$ solute center-of-mass coordinates with the $x$ and $y$ coordinates relative
	to the nearest pore center (b) Next, we convert the $x$ and $y$ 	
	coordinates to radial coordinates, $r$, then fix the state sequence and use the inference 
	component of the IHMM in order to estimate the parameters in terms of $r$ and $z$. Note that
	the segment colors in (b) are the same as (a) because we fixed the state sequence.
	(c) After clustering the VAR parameters and reassigning the state sequence so that segments 
	which belong to the same cluster are labeled the same across all solute trajectories, we subtract
	the mean of each segment, obtained before clustering, in order to zero out the
  	trajectory, and then fix the clustered state sequence to infer the parameters of each clustered 
  	state, assuming a mean of zero for all states. Note that the colors are no longer aligned with 
  	figures (a) and (b) because the states are relabeled in terms of their clusters. There are
  	also significantly less states in this single trajectory.
	}\label{fig:hmm_demo}
  \end{figure}

  \newpage

  \section{Parameter Convergence}\label{section:convergence}

  Given enough data, parameter estimates converge within only a few steps. In 
  Figure~\ref{fig:convergence}, we plot the entries of $A$ and $\Sigma$ as 
  a function of IHMM iteration. Some states are sampled far more frequently
  than others. High sampling frequently results in higher certainty converged
  parameter estimates.

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.7\textwidth}
  \includegraphics[width=\textwidth]{convergence_MET_4.pdf}
  \caption{15 total emissions}\label{fig:convergence_MET_low}
  \end{subfigure}
  \begin{subfigure}{0.7\textwidth}
  \includegraphics[width=\textwidth]{convergence_MET_21.pdf}
  \caption{1289 total emissions}\label{fig:convergence_MET_medium}
  \end{subfigure}
  \begin{subfigure}{0.7\textwidth}
  \includegraphics[width=\textwidth]{convergence_MET_15.pdf}
  \caption{24468 total emissions}\label{fig:convergence_MET_high}
  \end{subfigure}
  \caption{As the total number of emissions observed from each state
  increases, the uncertainty in the converged parameters estimates
  decreases.}\label{fig:fixed_state_convergence}
  \end{figure}

  \newpage

  \section{Choosing Prior Parameters}\label{section:prior_guesses}

  The states identified by the IHMM are heavily influenced by the Gaussian prior
  placed on $\mathbf{c}$ in Equation~\ref{M-eqn:var} of the main text. The 
  entries of $A$ and $\Sigma$ do not vary over a wide range, so the final
  parameters were relatively insensitive to the priors. In order to 
  maximally automate the IHMM procedure, we attempted to parameterize the
  prior on $\mathbf{c}$ in an intelligent way. The prior parameters should
  be chosen such that the mean level of each state lies within a region of 
  reasonable probability of the prior (see Figure~\ref{fig:prior_guesses}).
  In each dimension, we defined the prior mean to lie halfway between the 
  maximum and minimum of each trajectory dimension. To parameterize the 
  prior's variance in each dimension, we defined the maximum and minimum to 
  be 2 standard deviations from the prior mean. Although this approach has 
  worked quite well for the data in this work, it is important to check the 
  results to determine whether further adjustments to the prior might be needed.
  In Figure TBD, we show the result of a parameterization where the prior
  parameters of $c$ were poorly chosen. %TODO

  \begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{prior_guesses.pdf}
  \caption{The parameters of the prior on the mean vector, $c$, (black line), which
  represents the coordinates at which solute are trapped, should be chosen such
  that the mean levels of each state identified in the trajectory (blue line) lie within
  regions of the prior with reasonable probability. We chose the mean of the prior 
  as halfway between the maximum and minimum of each trajectory dimension. We chose 
  $\sigma$ of the prior by defining the maximum and minimum to be 2 standard deviations
  from the mean (dashed lines).}\label{fig:prior_guesses}
  \end{figure}

  \newpage

  \section{Agglomerative Clustering Versus Gaussian Mixture Models}\label{section:agglomerative}

  % BJC: will show Gaussian mixture model which has a cluster engulfing another cluster, so
  % it's tails are on both sides of the center cluster.

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.95\textwidth}
  \includegraphics[width=\textwidth]{bayesian_A.pdf}
  \caption{Bayesian Gaussian mixture model}\label{fig:bayesian_A}
  \end{subfigure}
  \begin{subfigure}{0.95\textwidth}
  \includegraphics[width=\textwidth]{agglomerative_A.pdf}
  \caption{Agglomerative Clustering}\label{fig:agglomerative_A}
  \end{subfigure}
  \caption{To reduce the state space, we prefer agglomerative clustering over Bayesian
  Gaussian mixture modeling. In the plots above we show the results of clustering the
  diagonal entries of the autoregressive coefficient matrices, $A$, of methanol. (a) 
  Bayesian Gaussian mixture models tend to delocalize the clusters in parameter space
  since the Gaussians can overlap. Agglomerative clustering prevents overlap of 
  clusters and ensures that all states within each cluster have similar parameters.
  }\label{fig:clustering_choice}
  \end{figure}

  \newpage

  \section{Choosing the Number of Clusters}\label{section:nclusters}

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_MET.pdf}
  \caption{methanol}\label{fig:silhouette_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_URE.pdf}
  \caption{urea}\label{fig:silhouette_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_GCL.pdf}
  \caption{ethylene glycol}\label{fig:silhouette_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{silhouette_ACH.pdf}
  \caption{acetic acid}\label{fig:silhouette_ACH}
  \end{subfigure}
  \caption{We used the silhouette score test in order to quantitatively
  inform our decision on the numbrer of clusters. Silhouette scores 
  closer to one indicate good clustering. The crosses on the plot indicate
  our choice in number of clusters after careful consideration of the
  silhouette scores in conjunction with qualitative examination of the clusters
  formed by the choice. Although the test often
  favors fewer states, we elected use intermediate number of states in 
  the cases of $A$ and $\Sigma$ because choosing 2--3 clusters 
  insufficiently separates the dynamical modes. }\label{fig:silhouette}
  \end{figure}

\end{document}

### 2020-04-10 Ben_Manuscripts/hdphmm/Draft.tex
comments.

@@
   % an abbreviated form for my dissertation. I'll work on the intro after my defense.  
+  %MRS7: sounds good, I won't look at this today.
 
@@
 
-  In our previous work, we designed two different approaches which used
+  In our previous 
+%MRS:work
+study,
+  we designed two different approaches which used
   solute time series in order to parameterize stochastic models that could be used
@@
   We let each solute undergo 5 $\mu$s of MD simulation. We used a time step of 2 fs
-  at a pressure of 1 bar and temperature of 300K controlled by the Parinello-Rahman 
-  barostat and v-rescale thermostat respectively. We recorded frames every 0.5 ns.
+  at a pressure of 1 bar and temperature of 300K controlled by the Parrinello-Rahman 
+  barostat~\cite{???} and velocity rescale thermostat~\cite{???} respectively. We recorded configurations every 0.5 ns.
 
@@
   %(see Figure~\ref{fig:cartesian_cylinder}). 
-  By working in cartesian coordinates, we avoid
+  By working in Cartesian coordinates, we avoid
   mathematical complexity introduced by cylindrical coordinates while estimating the 
@@
 %  \centering
-%  %MRS3: does this preserve the z-axis symmmetry? Is it just ensuring
-%  %that you can't jump that far, or is it limitinig the values that
+%  %MRS3: does this preserve the z-axis symmetry? Is it just ensuring
+%  %that you can't jump that far, or is it limiting the values that
 %  %the mean can take? Apologies if it's not clear to me yet.  I'm
@@
   Although the IHMM is capable of identifying an infinite number of states, 
-  a Dirichlet Process tends to exhibit a ``rich get richer" effect, favoring
+  a Dirichlet process tends to exhibit a ``rich get richer" effect, favoring
   a fewer number of states. By applying the algorithm to each trajectory 
@@
   $y$ center-of-mass coordinates to $r$. We fixed the state sequence from the 
-  3D parmeterization and applied the inference component of the IHMM procedure
+  3D parameterization and applied the inference component of the IHMM procedure
   to the cylindrical trajectories in order to estimate the VAR(1) parameters in
@@
   We elected to choose the number of clusters rather than the distance threshold.
-  For our data, non-parameteric methods such as Bayesian Gaussian mixture models tend
+  For our data, non-parametric methods such as Bayesian Gaussian mixture models tend
   to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
@@
   the Supporting Information). However, choosing too few clusters tends to 
-  result in inadequate distinguishment between visually obvious differences in 
+  not distinguish between visually obvious differences in 
   dynamic behavior. This results in finalized parameter sets that are averages of
@@
   $z$) solute trajectories so that they had a mean of zero, leaving only the 
-  fluctations. We did this by the mean of each same-state segment of the 
+  fluctuations. We did this by the mean of each same-state segment of the 
   unclustered trajectory. We used the IHMM algorithm on this modified trajectory
@@
   A, atoms is less than 3.5\AA~and the angle formed by $D-H \cdots A$ is less than 
-  30 $\degree$.~\cite{luzar_effect_1996}
+  $30\degree$.~\cite{luzar_effect_1996}
 
@@
   the system in the +/- x, y and z directions and then chose the bounds on the
-  histogram in order to create a rectanglular box encompassing the unitcell with
+  histogram in order to create a rectangular box encompassing the unit cell with
   a 1 nm buffer between the histogram and unit cell boundaries. We then used a regular
-  grid interpolator in order to allow interpolation at arbitray points within the grid.
-
-  We quantified solute motion using the time averaged mean squared displacment (MSD)
+  grid interpolator in order to allow interpolation at arbitrary points within the grid.
+
+  We quantified solute motion using the time averaged mean squared displacement (MSD)
   of the solute center of mass trajectories. The time-averaged MSD measures all observed
@@
   modes for each solute. Many of these modes are sampled very infrequently and thus
-  do not contribute signficantly to a general understanding of solute transport behavior.
+  do not contribute significantly to a general understanding of solute transport behavior.
   In this section, we explore a subset of this data, focusing on the states
@@
 
+  %MRS7: more descriptive title?  What about methanol?
   \subsubsection*{The Case of Methanol}
@@
   %MRS6: likely just the summary of the methanol behavior should go in the main paper - the rest should be SI.
-  Methanol exhbits a range of dynamic behavior. In Figure~\ref{fig:mechanism_map}, we
+  Methanol exhibits a range of dynamic behavior. In Figure~\ref{fig:mechanism_map}, we
   plot a representative 2D methanol trajectory in cylindrical coordinates. The coordinates
@@
   behaviors (in order of their first appearance, they are colored dark yellow, red, light
-  blue, light green, orange, blue, teal and lime green). The solute timeseries are coupled
+  blue, light green, orange, blue, teal and lime green). The solute time series are coupled
   with color coded bars which describe the solute's local environment and physical 
@@
   correspond to hydrogen bonds donated to the monomer's carboxylate head group. Green slivers
-  corrrespond to  hydrogen bonds donated to the ether linkages between the head groups
+  correspond to  hydrogen bonds donated to the ether linkages between the head groups
   and tails. Red slivers correspond to hydrogen bonds donated to the oxygens on the ends
@@
   by the frequent state changes during that time period and red slivers in the bar
-  above. Signficant hops in the $z$ direction appear to be described by the dark blue
+  above. Significant hops in the $z$ direction appear to be described by the dark blue
   state. After entering the dark blue state ca. 850 ns, methanol appears to jump
-  signficantly in the $z$ direction from a hydrogen bonded state with the ether 
+  significantly in the $z$ direction from a hydrogen bonded state with the ether 
   linkages to a hydrogen bonded state with a head group in a monomer below it.
@@
   can analyze each segment sequentially and form a clear picture of this instance of 
-  methanol's behavior without the need to visulize the traejectory with software like VMD.
+  methanol's behavior without the need to visualize the trajectory with software like VMD.
   However, it is still possible to gain a more general understanding of methanol's average
@@
   4 and 6 are in the viscous tail region, their dwell times are only intermediate. This
-  could be due to imhomogeneity in the tail region which causes transitions between many
-  different trapped states but with litle net effect on solute MSD. However, there are
+  could be due to inhomogeneity in the tail region which causes transitions between many
+  different trapped states but with little net effect on solute MSD. However, there are
   instances of states within the tail region with dwell times that exceed 100--200 ns,
@@
   It's dwell time of ca.~8 ns, suggests that solutes stay in this highly mobile 
-  state for long enough for their positions to displace signficantly.
+  state for long enough for their positions to displace significantly.
 
@@
   \begin{subfigure}{0.35\textwidth}
-  % BJC: I'll bootstrap some errorbars on this by drawing the transition probabilities 
-  % from a dirichlet distribution.
+  % BJC: I'll bootstrap some error bars on this by drawing the transition probabilities 
+  % from a Dirichlet distribution.
   \includegraphics[width=\textwidth]{A_sigma_scatter_MET.pdf}
@@
   The $y$-axis labels of the $r$ coordinate plot specify the radial mean of each clustered 
-  state. The percentage of trajectories in which the states appear are labeled to the right of
+  state. 
+  %MRS7: it's confusing to have the R not in order of r.
+Emphasize this more in the caption, maybe think of something a bit different for the final paper.
+Reads odd to have numbers not in order along an axis.
+The percentage of trajectories in which the states appear are labeled to the right of
   the $r$ plots. States 1--5 appear in the trajectory shown in Figure~\ref{fig:mechanism_map}
@@
   parameters. States 1 and 2 have higher covariances in both the axial and radial directions compared
-  to all other states. This should lead to signficant solute displacement. Covariance in each dimension
+  to all other states. This should lead to significant solute displacement. Covariance in each dimension
   appears to have a strong correlation. States 3--6 all have relatively low covariances, which may
@@
   out of the state with probability 1 - p. Of the prevalent states, states 1 and 
-  2 exhbit the shortest dwell times alongside their high covariances. States 5 and 7 have the longest dwell times in the pore and tail regions respectively.
+  2 exhibit the shortest dwell times alongside their high covariances. States 5 and 7 have the longest dwell times in the pore and tail regions respectively.
   }\label{fig:common_states_MET}
@@
   location (see Figure~\ref{fig:hbond_pichart}). States with radial means near 1 nm
-  or less (states 1, 3 and 5) typcially hydrogen bond with the monomer carboxylate
+  or less (states 1, 3 and 5) typically hydrogen bond with the monomer carboxylate
   groups and ether linkages. States with radial means greater than 1 nm (states 2,
@@
   of hydrogen bonds. Conversely, methanol molecules trapped in state 7 are in the densest 
-  region of all states studied. It is likely difficult for methanol to esacpe these high 
+  region of all states studied. It is likely difficult for methanol to escape these high 
   density regions and its position is further stabilized via hydrogen bonding.
 
-  %BJC4: I didn't put sodium ion assocaition in this figure because it's infrequent. 
+  %BJC4: I didn't put sodium ion association in this figure because it's infrequent. 
   %BJC4: If I compare to acetic acid or urea, I could add it back. I was thinking of splitting
@@
   \end{subfigure}
-  \caption{(a) Methanol hydrogen bonds with different segements of the LLC monomer
+  %MRS7: should it be ``methanol hydrogen bonding in different segments''? 
+  \caption{(a) Methanol hydrogen bonds with different segments of the LLC monomer
+    %MRS7: why are some wedges bigger? (green on 2 and 6 for example)
   dependent on the state. States with mean radial locations in the pore region tend to
@@
   hydrogen bond lifetimes of methanol in states with radial means in the tail
-  region tend to increase with local density and mean dwell times. This monotonic
+  region tend to increase with local density and mean dwell times. 
+  %MRS7: not clear from graphic which ones are in the pore.
+  %MRS7: is there any legend for the color for b? If same as above figure, indicate. Don't REALLY need color since they bars are already labeled, so it's 2 sources of duplicate information.
+  %MRS7: cross-hatching doesn't appear in the legend? Not sure which is which (I assume hatched is number density because closer to that axis).
+  This monotonic
   relationship does not exist for states in the pore region. The high 
@@
   \end{subfigure}
+  %MRS7: maybe in dwell time legend, say ``Max dwell in'' instead of ``Max of''
   \begin{subfigure}{0.45\textwidth}
@@
   \end{subfigure}
+  %MRS7: is c) methanol?  I thought it wasn't associating with Na+ much.
+  %MRS7: methanol yellow is hard to see in c)
   \caption{(a) Solutes hydrogen bond and associate with sodium ions
@@
   after a 1000 ns time lag. (b) We histogrammed the means of the clusters weighted
-  by the number of emissions from that cluster. Most solutes spend the majority of
+  by the number of 
+  %MRS7: ``transitions out'' instead of emisssions?
+  emissions from that cluster. Most solutes spend the majority of
   their time close to the pore center. Only methanol has a significant peak
@@
     what one might consider the pore and tail region, most evident in methanol's 
-    distribution of radial positons.
+    distribution of radial positions.
     \item The area between the head groups and the distal regions of the tails is
@@
     in order to transition to that region.
-    %BJC: I wonder if there is a state which corresponds to the jump from pore to tail region. MIght be hard to pick up.
+    %BJC: I wonder if there is a state which corresponds to the jump from pore to tail region. Might be hard to pick up.
     \item Methanol is the smallest solute in this study and therefore appears to 
@@
     \item Although urea possesses the state with the longest dwell time among the
-    solutes studied, it occurs in the tail region with prevelant states having 
+    solutes studied, it occurs in the tail region with prevalent states having 
     much shorter dwell times.  %BJC: get radius of long entrapment.
@@
 Can also use this to test new strategies.
-  %MRS6: toy data is actually a VERY good idea.  USe a VAR process that looks like MD, and then try to cluster it, and figure out why different.
+  %MRS6: toy data is actually a VERY good idea.  Use a VAR process that looks like MD, and then try to cluster it, and figure out why different.
 
@@
   of the IHMM model. 
-  %MRS6: definitely an important poiint for the paper: clustering things togethere might make trajectories too typical.
+  %MRS6: definitely an important point for the paper: clustering things together might make trajectories too typical.
   Some trajectories span a wide range of $z$ coordinates, while others stay
@@
   clustered as their own, but the transition probabilities would have high uncertainties.
-        %MRS6: is it necessarily a problem that the transition probabiblities have high uncertainties?
-If one is drawing from the Dirichlet distribution, uncertainy isn't a big deal.
+        %MRS6: is it necessarily a problem that the transition probabilities have high uncertainties?
+If one is drawing from the Dirichlet distribution, uncertainty isn't a big deal.
 The trapping just doesn't quite seem to be as long as MD.
-        %MRS6: the other issue is apparent surpression on variance in the jumps, but that may be harder to get. 
+        %MRS6: the other issue is apparent suppression on variance in the jumps, but that may be harder to get. 
   It is also possible that we should not be using a static transition matrix in 
@@
   %BJC5: TODO: redo these plots with r clusters
-  \caption{We can generate trajectories which bear some qualitative resemblence to the MD 
+  %MRS7: still odd it doesn't stay at large r.
+  %MRS7: can you restart the radial coordiante, so 0-3 just repeats, instead of going up tp 17.5?
+ \caption{We can generate trajectories which bear some qualitative resemblance to the MD 
   trajectories. Solute trajectories generated by our model (blue) show the same
@@
   the state space to 10\% of its original size by grouping states with similar VAR
-  parmeters.
+  parameters.
 
@@
   of the diverse sets behavior exhibited by solutes in these membranes. We showed how
-  solute motion is influenced by hdyrogen bonding, sodium ion association and local
+  solute motion is influenced by hydrogen bonding, sodium ion association and local
   membrane density. These interactions have a direct impact on the size and
@@
   characteristic of polar solutes in this system. We can also use them to reproduce
-  the solute MSDs measured from the MD traejectories. The low computational expense 
+  the solute MSDs measured from the MD trajectories. The low computational expense 
   of generating these stochastic trajectories allows one to project solute behavior
@@
 \end{document}
+
+% LocalWords:  BJC micropollutants Desalination permeability nanofiltration LLC
+% LocalWords:  Amphiphilic nanostructures Lyotropic amphiphilic lyotropic MSDDM
+% LocalWords:  solutes selectivities solute nanoscopic timescales MSDs MSD HMMs
+% LocalWords:  nonparameteric Parrinello Rahman barostat rescale transitioning
+% LocalWords:  al's HMM Dirichlet HDP DP Wishart TODO SI al MATLAB teh gael pdf
+% LocalWords:  nonparametric bayesian solute's reparameterized intracluster ca
+% LocalWords:  delocalize Luzar Chandler histogrammed interpolator methanol's
+% LocalWords:  nanostructure carboxylate VMD nonidealities hbonds outlier GAANN
+% LocalWords:  autogregressive PRF ACS XSEDE ACI

### 2020-04-13 Ben_Manuscripts/hdphmm/Draft.tex
add.
Added missing intro figs

@@
 \doublespacing
-
+%\DeclareUnicodeCharacter{03C9}{$\omega$}
 \externaldocument[S-]{Supporting_Information}
@@
   \maketitle
-
-  % BJC2: I'm not putting a lot of effort into the introduction since I'll only write
-  % an abbreviated form for my dissertation. I'll work on the intro after my defense.  
-  %MRS7: sounds good, I won't look at this today.
 
@@
 
-  In our previous 
-%MRS:work
-study,
-  we designed two different approaches which used
+  In our previous study, we designed two different approaches which used
   solute time series in order to parameterize stochastic models that could be used
@@
   In this work we attempt to minimize human effort by applying the infinite hidden 
-  Markov Model (IHMM), a nonparameteric Bayesian classification technique, in order to 
-  automatically detect and infer the parameters of an unknown number of latent
-  autoregressive (AR) modes present in solute center-of-mass time series trajectories.
+  Markov Model (IHMM)~\cite{beal_infinite_2002,calderon_inferring_2015}, a nonparameteric 
+  Bayesian classification technique, in order to automatically detect and infer the 
+  parameters of an unknown number of latent autoregressive (AR) modes present in solute
+  center-of-mass time series trajectories.
   We aim to address two primary scientific questions with this work. First, we want
@@
   exhibited by MD. We quantitatively validate these trajectories by comparing 
-  their mean squared displacement (MSD) to MSDs measured by MD.
+  their mean squared displacement (MSD) to those measured by MD.
 
@@
 
-  We ran all MD simulations and energy minimizations using GROMACS 2018. Our 
-  python implementation of the IHMM algorithm is available online at 
+  We ran all MD simulations and energy minimizations using GROMACS 2018.
+  ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}  
+  Our python implementation of the IHMM algorithm is available online at 
   \texttt{https://github.com/bencoscia/hdphmm}. All other post-simulation 
@@
   We chose to study a subset of 4 of the fastest moving solutes from our previous
-  work: methanol, acetic acid, urea and ethylene glycol. In addition to exploring
-  membrane structural space the most, these solutes have a relatively diverse set
-  of chemical functionality. For each solute we created a separate system and to 
+  work: methanol, acetic acid, urea and ethylene glycol.
+  In addition to exploring membrane structural space the most, these solutes have a
+  relatively diverse set of chemical functionality. For each solute we created a 
+  separate system and to 
   each system we added 6 solutes per pore for a total of 24 solutes. This number 
@@
   at a pressure of 1 bar and temperature of 300K controlled by the Parrinello-Rahman 
-  barostat~\cite{???} and velocity rescale thermostat~\cite{???} respectively. We recorded configurations every 0.5 ns.
+  barostat~\cite{parrinello_polymorphic_1981} and velocity rescale 
+  thermostat~\cite{bussi_canonical_2007} respectively. We recorded configurations every 0.5 ns.
 
@@
   testing a range of numbers of hidden states and determining which is the best 
-  representation of the data.
+  representation of the data.~\cite{pohle_selecting_2017}
 
@@
   The infinite-state HMM overcomes this drawback by placing a hierarchical
-  Dirichlet process (HDP) prior on the transition probabilities. Using some 
+  Dirichlet process (HDP) prior on the transition probabilities.~\cite{fox_bayesian_2010} Using some 
   base probability distribution, $H$, a Dirichlet process (DP) generates discrete 
@@
   $\beta_k$ come from a stick-breaking process parameterized by the concentration 
-  parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). In shorthand, this
+  parameter $\gamma$ (equivalently referred to as GEM($\gamma$)).~\cite{halmos_random_1944} In shorthand, this
   specification can be expressed as $G_0 \sim DP(\gamma, H)$. The concentration 
@@
 
-  % BJC2: It might be useful to walk through the following procedure with an example 
-  % trajectory
-  % TODO in the SI
-
   %Based on the algorithms developed by Fox et al.~\cite{fox_sticky_2007}, 
@@
   as the $A$ and $\Sigma$ matrices of Equation~\ref{eqn:var}. We detected equilibration 
-  of the parameters using the module \texttt{pymbar.timeseries.detect\_equilibration} on
+  of the parameters using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} on
   the time series of parameter estimates. Plots illustrating parameter convergence are 
@@
   pore center as the origin, we represented the radial distance of each solute's 
-  center-of-mass from the pore center in 2 dimensions, $x$ and $y$ 
+  center-of-mass from the pore center in 2 dimensions, $x$ and $y$.
   %(see Figure~\ref{fig:cartesian_cylinder}). 
@@
   a Dirichlet process tends to exhibit a ``rich get richer" effect, favoring
-  a fewer number of states. By applying the algorithm to each trajectory 
+  a fewer number of states.~\cite{dreyer_discovering_2011} By applying the algorithm to each trajectory 
   independently, we reduce the possibility of lumping together multiple 
@@
   We ran 2000 iterations of the IHMM procedure in order to arrive at converged 
-  state sequences and parameters for each state. Most parameters converged 
-  quickly (within 50-100 iterations) while others took up to 1000 iterations.
-  %BJC6: still need to make these figures.
+  state sequences. We evaluated the convergence of the state sequence based on
+  the convergence of the VAR parameters. The parameters of each states
+  generally converge within 500--1000 iterations. However, the boundaries of 
+  each state segment fluctuate which can lead to high variance in the $A$
+  and $\Sigma$ parameters in segments with a relatively low number of emissions.
+  In these cases, the mean in each dimension tends to be a more reliable indicator of
+  convergence (see Figure~\ref{S-fig:convergence3d} of the Supporting Information).
+
   We defined the finalized parameters of each state as the average of the 
@@
   equilibration time of all dimensions as the equilibration time point.
-  Further details are available in Section~\ref{S-section:convergence} of
-  the Supporting Information.
+%  Further details are available in Section~\ref{S-section:convergence} of
+%  the Supporting Information.
 
@@
   terms of $r$ and $z$. Since we fixed the state sequence, and we are using conjugate
-  priors, the VAR parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}). Therefore, we only ran 
-  the inference procedure for 100 iterations. 
+  priors, the VAR parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}).
+  Therefore, we only ran the inference procedure for 100 iterations. 
   %However, note that the uncertainty in their
@@
   similar clusters until a desired intracluster distance threshold or number of
-  clusters is reached. We used the Ward linkage criteria, which works to minimize 
-  the sum of the squared differences within all clusters.
+  clusters is reached.~\cite{pedregosa_scikit-learn_2011} We used the Ward linkage criteria, which works to minimize 
+  the sum of the squared differences within all clusters.~\cite{ward_hierarchical_1963}
     %MRS6: explain why Ward (make the cluster as minimally disperse?)
@@
   We elected to choose the number of clusters rather than the distance threshold.
-  For our data, non-parametric methods such as Bayesian Gaussian mixture models tend
+  For our data, non-parametric methods such as Bayesian Gaussian mixture models~\cite{pedregosa_scikit-learn_2011,gelman_bayesian_2013} tend
   to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
@@
   test in order to score the quality of clustering as a function of the number 
-  of clusters chosen. For our data, the silhouette test generally favors the 
+  of clusters chosen.~\cite{kaufman_finding_2009} For our data, the silhouette test generally favors the 
   lowest number of clusters possible (see Section~\ref{S-section:nclusters} of
@@
   $z$) solute trajectories so that they had a mean of zero, leaving only the 
-  fluctuations. We did this by the mean of each same-state segment of the 
+  fluctuations. We did this by subtracting the mean from each same-state segment of the 
   unclustered trajectory. We used the IHMM algorithm on this modified trajectory
@@
   with our previous work, we reported the 95th percentile of hydrogen bond lifetimes
-  since their distribution is not Gaussian and to emphasize longer trapping periods.
+  since their distribution is not Gaussian and to emphasize longer trapping periods.~\cite{coscia_chemically_2019}
 
@@
   histogram in order to create a rectangular box encompassing the unit cell with
-  a 1 nm buffer between the histogram and unit cell boundaries. We then used a regular
-  grid interpolator in order to allow interpolation at arbitrary points within the grid.
+  a 1 nm buffer between the histogram and unit cell boundaries.~\cite{van_der_walt_numpy_2011} We then used a regular
+  grid interpolator in order to allow interpolation at arbitrary points within the grid.~\cite{virtanen_scipy_2020}
 
   We quantified solute motion using the time averaged mean squared displacement (MSD)
-  of the solute center of mass trajectories. The time-averaged MSD measures all observed
+  of the solute center of mass trajectories.~\cite{meroz_toolbox_2015} The time-averaged MSD measures all observed
   displacements over time lag $\tau$:
@@
 
-  %MRS7: more descriptive title?  What about methanol?
-  \subsubsection*{The Case of Methanol}
-
-  %MRS6: likely just the summary of the methanol behavior should go in the main paper - the rest should be SI.
+  \subsubsection*{The Dynamics of Methanol}
+
   Methanol exhibits a range of dynamic behavior. In Figure~\ref{fig:mechanism_map}, we
@@
   are colored according to the cluster with which methanol's dynamics are most consistent,
-  which implies that this particular methanol trajectory exhibits 8 distinct dynamical 
+  which implies that this particular methanol trajectory exhibits eight distinct dynamical 
   behaviors (in order of their first appearance, they are colored dark yellow, red, light
@@
   can analyze each segment sequentially and form a clear picture of this instance of 
-  methanol's behavior without the need to visualize the trajectory with software like VMD.
+  methanol's behavior without the need to visualize the trajectory with software like VMD.~\cite{humphrey_vmd:_1996}
   However, it is still possible to gain a more general understanding of methanol's average
@@
   state. 
-  %MRS7: it's confusing to have the R not in order of r.
-Emphasize this more in the caption, maybe think of something a bit different for the final paper.
-Reads odd to have numbers not in order along an axis.
+  %MRS7: it's confusing to have the R not in order of r. Emphasize this more in the caption, 
+  %maybe think of something a bit different for the final paper. Reads odd to have numbers not in order along an axis.
+  %BJC7: indeed
   The percentage of trajectories in which the states appear are labeled to the right of
@@
   \end{subfigure}
-  %MRS7: should it be ``methanol hydrogen bonding in different segments''? 
-  \caption{(a) Methanol hydrogen bonds with different segments of the LLC monomer
-    %MRS7: why are some wedges bigger? (green on 2 and 6 for example)
+  \caption{(a) Methanol hydrogen bonds in different segments of the LLC monomer
   dependent on the state. States with mean radial locations in the pore region tend to
@@
   molecules can help us to understand dynamical states in terms of membrane 
-  interactions. States 1 and 2, which have large covariances, also have short
+  interactions. The bars are colored according to match the states in Figures~\ref{fig:mechanism_map}
+  and~\ref{fig:common_states_MET}. States 1 and 2, which have large covariances, also have short
   hydrogen bond lifetimes and exist in relatively low density regions. The
@@
   %MRS7: is there any legend for the color for b? If same as above figure, indicate. Don't REALLY need color since they bars are already labeled, so it's 2 sources of duplicate information.
+  %BJC7: The state numbers are all you need to compare to the previous figure BUT the color make it easier 
+  %plot of the methanol trajectory where states aren't labeled.
   %MRS7: cross-hatching doesn't appear in the legend? Not sure which is which (I assume hatched is number density because closer to that axis).
+  %BJC7: Is it because the hatches aren't dense enough? I see them in the legend
   This monotonic
@@
   We applied the IHMM to the other three solutes in this study: urea, acetic acid
-  and ethylene glycol. 
-  \begin{itemize}  
-    \item Not only can we use the model to study the dynamics of each solute 
-    individually, but we can compare their behavior in order to improve our
+  and ethylene glycol. Not only can we use the model to study the dynamics of each 
+  solute individually, but we can compare their behavior in order to improve our
   understanding of more subtle mechanistic details.
-  \end{itemize}
 
   The size and chemical functionality of the solutes dictates the interactions which
-  influence solute transport. 
-  \begin{itemize}  
-    \item In Figure~\ref{fig:hbonds_assoc_summary}, we show that the solutes 
-    donate hydrogen bonds and associate with sodium ions to varying degrees.
-    \item We also show the solute MSDs after a 1000 ns time lag. 
-    \item It is not immediately obvious why the MSDs follow this trend.
-    \item The states identified by the IHMM can help us shed some light.
-  \end{itemize}
+  influence solute transport. In Figure~\ref{fig:hbonds_assoc_summary}, we show that
+  the solutes donate hydrogen bonds and associate with sodium ions to varying degrees.
+  We also show the solute MSDs after a 1000 ns time lag. It is not immediately obvious
+  why the MSDs follow this trend. The states identified by the IHMM shed
+  some light on the reasoning.
 
@@
   \end{subfigure}
-  %MRS7: maybe in dwell time legend, say ``Max dwell in'' instead of ``Max of''
   \begin{subfigure}{0.45\textwidth}
@@
   %MRS7: is c) methanol?  I thought it wasn't associating with Na+ much.
+  %BJC7: looks about 5 %, certainly less than the other. I could add
+  % some discussion of this to previous section.
   %MRS7: methanol yellow is hard to see in c)
@@
   after a 1000 ns time lag. (b) We histogrammed the means of the clusters weighted
-  by the number of 
-  %MRS7: ``transitions out'' instead of emisssions?
-  emissions from that cluster. Most solutes spend the majority of
+  by the number of fluctuation within that cluster. Most solutes spend the majority of
   their time close to the pore center. Only methanol has a significant peak
@@
   Hydrogen bonding and sodium ion association interactions are far more 
-  common when solutes stay near the pore centers.
-  \begin{itemize}
-    \item In Figure~\ref{fig:rdf_summary}, we plot the distribution of the 
-    radial means of each cluster weighted by the time spent in that cluster.
-    \item All solutes except methanol spend the majority of their time near
-    the pore centers (roughly defined as within 1.5 nm).
-    \item As we showed earlier, methanol spends a significant portion of its
+  common when solutes stay near the pore centers. In Figure~\ref{fig:rdf_summary},
+  we plot the distribution of the radial means of each cluster weighted by 
+  the time spent in that cluster. All solutes except methanol spend the 
+  majority of their time near the pore centers (roughly defined as within 
+  1.5 nm). As we showed earlier, methanol spends a significant portion of its
   time trapped in the dense tails.
-  \end{itemize}
 
@@
   Solute size likely has a large effect on their preferred radial location within
-  the pores.
-  \begin{itemize}
-    \item The histograms in Figure~\ref{fig:rdf_summary} have a clear vacancy between
-    what one might consider the pore and tail region, most evident in methanol's 
-    distribution of radial positions.
-    \item The area between the head groups and the distal regions of the tails is
-    dense and hydrophobic which creates a considerable energy barrier to be overcome
-    in order to transition to that region.
+  the pores. The histograms in Figure~\ref{fig:rdf_summary} have a clear vacancy 
+  between what one might consider the pore and tail region, most evident in methanol's 
+  distribution of radial positions. The area between the head groups and the distal
+  regions of the tails is dense and hydrophobic which creates a considerable energy 
+  barrier to be overcome in order to transition to that region.
   %BJC: I wonder if there is a state which corresponds to the jump from pore to tail region. Might be hard to pick up.
-    \item Methanol is the smallest solute in this study and therefore appears to 
+  Methanol is the smallest solute in this study and therefore appears to 
   have the easiest time crossing into the tails.
-  \end{itemize}
 
@@
   acid, ethylene glycol and urea exhibit a range of trapping behavior.
-  \begin{itemize}
-    \item It is clear that the number of polar interactions is not directly
+  It is clear that the number of polar interactions is not directly
   related to solute MSD. Acetic acid participates in a similar number of 
   interactions relative to urea and ethylene glycol, but its MSD is considerably
-    lower.
-    \item For the purpose of this analysis, as in the previous section, we 
+  lower. For the purpose of this analysis, as in the previous section, we 
   defined states that appear in more than one third of the trajectories to
-    be prevalent states.
-    \item In Figure~\ref{fig:dwell_time_summary}, we plot the longest dwell
-    times exhibited by each solute among the prevalent states as well 
-    as out of all the states.
-    \item The state which exhibits the longest dwell times among all acetic
-    acid states appears in 9 different trajectories, making it a prevalent state,
-    and occurs 1 nm from the pore center. %BJC: check exact radius
-    \item Although urea possesses the state with the longest dwell time among the
+  be prevalent states. In Figure~\ref{fig:dwell_time_summary}, we plot the\
+  longest dwell times exhibited by each solute among the prevalent states as 
+  well as out of all the states. The state which exhibits the longest dwell
+  times among all acetic acid states appears in 9 different trajectories, 
+  making it a prevalent state, and occurs 0.9 nm from the pore center.
+  Although urea possesses the state with the longest dwell time among the
   solutes studied, it occurs in the tail region with prevalent states having 
-    much shorter dwell times.  %BJC: get radius of long entrapment.
-    \item Ethylene glycol appears to be the least subject to trapping.
-  \end{itemize}
+  much shorter dwell times. Ethylene glycol appears to be the least subject to
+  trapping.
 
@@
   \includegraphics[width=\textwidth]{trajectory_realizations_MET.pdf}
-  %MRS5: maybe it would be good to put a dotted line through each of the centers of the offset trajectories?
-  %BJC5: TODO: redo these plots with r clusters
-  %MRS7: still odd it doesn't stay at large r.
-  %MRS7: can you restart the radial coordiante, so 0-3 just repeats, instead of going up tp 17.5?
   \caption{We can generate trajectories which bear some qualitative resemblance to the MD 
@@
   The MSDs calculated by stochastic realizations of our model are quantitatively similar to
-  MD. For all solutes except acetic acid, our predicted MSD curve lie close to but below the
+  MD. For all solutes except acetic acid, our predicted MSD curves lie close to but below the
   1$\sigma$ confidence intervals of MD. However, in these cases, the average MD MSDs are 
@@
   Detailed explanations and expansions upon the results and procedures mentioned in
-  the main text are described in the Supporting Information. This information is
-  available free of charge via the Internet at http://pubs.acs.org.
+  the main text are described in the Supporting Information. 
+  %This information is
+  %available free of charge via the Internet at http://pubs.acs.org.
 
@@
 
-  %MRS2: add GAANN and PRF here to cover bases.
   This work was supported in part by the ACS Petroleum Research Fund

### 2020-04-13 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Added missing intro figs

@@
   	pore center (see Figure~\ref{fig:xyz_hmm}). 	
-  	\item Convert x and y coordinates to radial coordinates, $r$, then fix the state sequence
+  	\item Convert $x$ and y coordinates to radial coordinates, $r$, then fix the state sequence
   	and use the inference component of the IHMM in order to estimate the parameters in terms
@@
   	figures (a) and (b) because the states are relabeled in terms of their clusters. There are
-  	also significantly less states in this single trajectory.
+  	also less states in this single trajectory.
 	}\label{fig:hmm_demo}
-  \end{figure}
-
-  \newpage
-
-  \section{Parameter Convergence}\label{section:convergence}
-
-  Given enough data, parameter estimates converge within only a few steps. In 
-  Figure~\ref{fig:convergence}, we plot the entries of $A$ and $\Sigma$ as 
-  a function of IHMM iteration. Some states are sampled far more frequently
-  than others. High sampling frequently results in higher certainty converged
-  parameter estimates.
-
-  \begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.7\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_4.pdf}
-  \caption{15 total emissions}\label{fig:convergence_MET_low}
-  \end{subfigure}
-  \begin{subfigure}{0.7\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_21.pdf}
-  \caption{1289 total emissions}\label{fig:convergence_MET_medium}
-  \end{subfigure}
-  \begin{subfigure}{0.7\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_15.pdf}
-  \caption{24468 total emissions}\label{fig:convergence_MET_high}
-  \end{subfigure}
-  \caption{As the total number of emissions observed from each state
-  increases, the uncertainty in the converged parameters estimates
-  decreases.}\label{fig:fixed_state_convergence}
   \end{figure}
@@
   results to determine whether further adjustments to the prior might be needed.
-  In Figure TBD, we show the result of a parameterization where the prior
-  parameters of $c$ were poorly chosen. %TODO
+%  In Figure TBD, we show the result of a parameterization where the prior
+%  parameters of $c$ were poorly chosen. %TODO
 
@@
   \includegraphics[width=\textwidth]{prior_guesses.pdf}
-  \caption{The parameters of the prior on the mean vector, $c$, (black line), which
+  \caption{The parameters of the prior on the mean vector, $\mathbf{c}$, (black line), which
   represents the coordinates at which solute are trapped, should be chosen such
@@
   regions of the prior with reasonable probability. We chose the mean of the prior 
-  as halfway between the maximum and minimum of each trajectory dimension. We chose 
+  as halfway between the maximum and minimum (shown by the dashed lines) of each trajectory dimension. We chose 
   $\sigma$ of the prior by defining the maximum and minimum to be 2 standard deviations
-  from the mean (dashed lines).}\label{fig:prior_guesses}
+  from the mean.}\label{fig:prior_guesses}
   \end{figure}
 
-  \newpage
+  \pagebreak
+
+  \section{Parameter Convergence}\label{section:convergence}
+
+  The state sequence appears to converge within 500--1000 IHMM iterations. Step 1
+  in the procedure from the previous section is the only time the state sequence 
+  is determined. We ran 2000 iterations of the IHMM algorithm in order to arrive
+  at a finalized state sequence. Stabilization of the VAR parameters indicates 
+  that the state sequence has converged. In Figure~\ref{fig:convergence3d}, we plot
+  the diagonal entries of 3 different $A$ and $\Sigma$ matrices as well as the 
+  entries of the mean vector $\mathbf{c}$, fit to a single 3D methanol trajectory.
+  States with a relatively small number of observations are more highly influenced 
+  by the boundaries of the state segments and generally lead to much higher 
+  variance of the $A$ and $\Sigma$ parameters. In these cases, the mean is
+  a more reliable indicator of convergence since stabilized means imply that the
+  fluctuations assigned to each state come from motion about a static location.
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.8\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_47.pdf}
+  \caption{706 total emissions}\label{fig:convergence3d_MET_low}
+  \end{subfigure}
+  \begin{subfigure}{0.8\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_36.pdf}
+  \caption{1000 total emissions}\label{fig:convergence3d_MET_medium}
+  \end{subfigure}
+  \begin{subfigure}{0.8\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_59.pdf}
+  \caption{201 total emissions}\label{fig:convergence3d_MET_high}
+  \end{subfigure}
+  \caption{Given a sufficient number of observations for a given mode, the VAR parameters
+  appear to converge within 500 -- 1000 iterations. States with too few observations
+  are more highly influenced by the boundaries of the state segments and generally
+  lead to much higher fluctuations in the VAR parameters.}\label{fig:convergence3d}
+  \end{figure}
+
+  \clearpage
+
+  When we fix the state sequence in subsequent steps of the procedure, parameter 
+  estimates converge within only a few steps. In Figure~\ref{fig:fixed_state_convergence}, we 
+  plot the entries of $A$ and $\Sigma$ as a function of IHMM iteration. Some states
+  are sampled far more frequently than others. High sampling frequently results in
+  higher certainty converged parameter estimates. Due to fast convergence, we only
+  run 100 iterations of the inference behavior when the state sequence is fixed.
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.6\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_4.pdf}
+  \caption{15 total emissions}\label{fig:convergence_MET_low}
+  \end{subfigure}
+  \begin{subfigure}{0.6\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_21.pdf}
+  \caption{1289 total emissions}\label{fig:convergence_MET_medium}
+  \end{subfigure}
+  \begin{subfigure}{0.6\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_15.pdf}
+  \caption{24468 total emissions}\label{fig:convergence_MET_high}
+  \end{subfigure}
+  \caption{The VAR parameters converge quickly when we fix the state
+  sequence. As the total number of emissions observed from each state
+  increases, the uncertainty in the converged parameters estimates
+  decreases.}\label{fig:fixed_state_convergence}
+  \end{figure}
+
+  \clearpage
 
@@
   formed by the choice. Although the test often
-  favors fewer states, we elected use intermediate number of states in 
+  favors fewer states, we elected to use an intermediate number of states in 
   the cases of $A$ and $\Sigma$ because choosing 2--3 clusters 

### 2020-04-13 Ben_Manuscripts/thesis/structure.tex
Added missing intro figs

@@
 
-  \begin{figure}[!htb]
-  \centering
-	\begin{subfigure}{0.45\linewidth}
-		\centering
-		\includegraphics[width=0.6\textwidth]{cartoon_pore.pdf}
-		\caption{}~\label{fig:undetailed_pore}
-	\end{subfigure}
-	\begin{subfigure}{0.45\linewidth}
-		\centering
-		\includegraphics[width=0.6\textwidth]{detailed_pore.pdf}
-		\caption{}~\label{fig:detailed_pore}
-	\end{subfigure} 
-    \caption{(a) Previous understanding of the pores are essentially speculations 
-    based on limited chemical and experimental data. (b) We use detailed molecular 
-    modeling in this paper in order to appropriately model the pore's complex architecture,
-    which is crucial to understanding the mechanism of solute transport. In both 
-    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
-  \end{figure}
-
+%  \begin{figure}[!htb]
+%  \centering
+%	\begin{subfigure}{0.45\linewidth}
+%		\centering
+%		\includegraphics[width=0.6\textwidth]{cartoon_pore.pdf}
+%		\caption{}~\label{fig:undetailed_pore}
+%	\end{subfigure}
+%	\begin{subfigure}{0.45\linewidth}
+%		\centering
+%		\includegraphics[width=0.6\textwidth]{detailed_pore.pdf}
+%		\caption{}~\label{fig:detailed_pore}
+%	\end{subfigure} 
+%    \caption{(a) Previous understanding of the pores are essentially speculations 
+%    based on limited chemical and experimental data. (b) We use detailed molecular 
+%    modeling in this paper in order to appropriately model the pore's complex architecture,
+%    which is crucial to understanding the mechanism of solute transport. In both 
+%    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
+%  \end{figure}
+% 
   In this chapter, we perform molecular modeling of the Col\textsubscript{h}

### 2020-04-13 Ben_Manuscripts/thesis/thesis.tex
add comments to abstract.
Added missing intro figs

@@
 \usepackage{graphicx}		% to insert figures
-%\usepackage{hyperref}		% PDF hyperreferences??
+\usepackage{hyperref}		% PDF hyperreferences??
 \usepackage{amsmath}
@@
   inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
-  a promising class of materials for selective separations. Our current understanding
-  of these systems is not sufficient to design them for specific applications. In 
-  this thesis, we use detailed atomistic molecular modeling in order to investigate 
-  structure and transport of solutes within LLC polymer membrane.
+  a promising class of materials for selective separations. There is a wide 
+  design space available for liquid crystal monomer design which may allow one to
+  tailor solute interactions within the membrane pores. Our currrent
+  understanding of these membrane is based primarily on experimental measurements
+  and macroscopic modeling which limits our insight and ability to design them 
+  for specific applications.
 
-  We begin by enhancing our understanding of the nanoscopic pore structure in order 
-  to ensure we appropriately model the chemical environment in the pores. We use radial
-  distribution functions and simulated X-ray diffraction patterns to quantify and 
-  understand the major structural features of the model.
+  In this thesis, I develop a detailed atomistic molecular model, maximally consistent
+  with experimental structural data, in order to investigate structure and transport
+  of solutes within LLC polymer membranes. I characterize the dynamics of water, sodium
+  ions and 20 small polar solutes within its pores. I present evidence which suggests that 
+  LLC membranes are characterized by a gradual, rather than abrupt, transition in 
+  composition from the primarily aqueous pore region to the hydrophobic monomer
+  tail region. Within this continuous and heterogeneous environment, solutes perform
+  intermittent hops between lengthy periods of entrapment. I show how transport rates
+  of these species are dependent not only on molecular size, but on chemical functionality
+  as well.
 
-  We use our carefully constructed molecular model in order to observe transport of
-  water, sodium ions and 20 small polar solutes within the pores of a lyotropic 
-  liquid crystal (LLC) membrane using atomistic molecular simulations. We 
-  observe that solutes perform intermittent hops between lengthy periods of 
-  entrapment and describe how transport of a species is dependent not only on 
-  molecular size, but on chemical functionality as well.
-
-  Based on our qualitative understanding of solute transport, we focus the remainder
-  of our efforts on the development of three different stochastic models which can be
-  used to generate realizations of solute trajectories with qualitative and quantitative 
-  dynamics similar to our MD solute trajectories. Mathematically modeling complex 
-  transport phenomena at the molecular level can be a powerful tool for connecting 
-  microscopic chemically-dependent solute motions that do not follow simple diffusive
-  behavior with macroscopic membrane performance.
-
+  In order to connect these microscopic chemically-dependent solute motions to
+  macroscopic membrane performance, I develop three different stochastic models 
+  of varying complexity.  
   First, using anomalous diffusion theory, we show how solute dynamics can be
@@
   the configurational states of the system as a Markov process where each state has 
-  distinct transport properties. Finally we implement a third approach,
-  called the infinite hidden Markov model, which is capable of automatically 
-  distinguishing an unknown number of hidden dynamical modes in multidimensional
-  solute time series. This model offers a flexibile approach to modeling solute
-  motion and helps us to uncover mechanisms with minimal human effort.
+  distinct transport properties. Finally apply the infinite hidden Markov model, 
+  an approach capable of automatically distinguishing and parameterizing an unknown 
+  number of hidden dynamical modes in multidimensional solute time series. This model
+  offers a flexibile approach to modeling solute motion and helps us to uncover 
+  mechanisms with minimal human effort.
+
   }
@@
 \dedication[Dedication]{	% NEVER use \OnePageChapter here.
-	To all of the fluffy kitties.
+	To my girls Jenna, Maclynn and Aria.
 	}
@@
   pushing me to do high quality science. I thank the entire Shirts group for 
-  their feedback and encouragement as well as for making our lab an enjoyable to work.
-  I thank Richard Noble and Douglas Gin for their guidance on past and present 
-  experimental research on LLC membranes. I also thank Michael McGrath, Gregory 
-  Dwulet and Sarah Dischinger, members of the Gin and Noble groups, for providing
-  invaluable experimental perspective. I thank Matthew Glaser for his 
-  contributions to my understanding of liquid crystal systems. Our first paper 
-  would not have been complete without his insight. I thank Joseph Yelk for his 
-  effort creating the X-ray diffraction code on which our first paper relied.
-  I thank Christopher Calderon for his guidance on applying Bayesian non-parametric
-  techniques to solute time series.
-%  I would like to acknowledge my financial support: The ACS Petroleum Research Fund
-%  grant \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN) 
-%  fellowship which is funded by the U.S. Department of Education. 
-%
-%  % BJC: This acknowledgement is how they want to be cited in papers. Could I
-%  % shorten it for this?
-%  Finally, I would like to acknowledge my high performance computing resources:
-%  Molecular simulations were performed using the Extreme Science and
-%  Engineering Discovery Environment (XSEDE), which is supported by National
-%  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
-%  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
-%  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
-%  which is supported by the National Science Foundation (awards ACI-1532235 and
-%  ACI-1532236), the University of Colorado Boulder, and Colorado State
-%  University. The Summit supercomputer is a joint effort of the University of
-%  Colorado Boulder and Colorado State University.
+  their feedback and encouragement as well as for making our lab an enjoyable
+  place to work. I thank Richard Noble and Douglas Gin for their guidance on past
+  and present experimental research on LLC membranes as well as their
+  students Michael McGrath, Gregory Dwulet and Sarah Dischinger, for providing 
+  invaluable experimental perspective. I thank
+  Matthew Glaser for his contributions to my understanding of liquid crystal systems.
+  Our first paper would not have been complete without his insight. I thank Joseph
+  Yelk for his effort creating the X-ray diffraction code on which our first paper
+  relied. Finally, I thank Christopher Calderon for his guidance on applying 
+  Bayesian non-parametric techniques to solute time series, allowing a leap in
+  the flexibility of our dynamical modeling approaches.
+
+  Outside of the University, I was fortunate enough to have full support of my
+  friends and family. Moving to Colorado was a big leap and I would not
+  have been successful without their encouragement.
 
@@
 % \LoFisShort	% use this only for 1-page Table of Figures
-% \emptyLoF	% use this if there is no List of Figures
+\emptyLoF	% use this if there is no List of Figures
 
 % \LoTisShort	% use this only for 1-page Table of Tables
-% \emptyLoT	% use this if there is no List of Tables
+\emptyLoT	% use this if there is no List of Tables
 
@@
 
-\graphicspath{{../transport/figures/}{../structure_paper/figures/}{../transport/supporting_figures/}{../stochastic_transport/figures/}{../stochastic_transport/supporting_figures/}}
+\graphicspath{{../transport/figures/}{../structure_paper/figures/}{../transport/supporting_figures/}{../stochastic_transport/figures/}{../stochastic_transport/supporting_figures/}{../hdphmm/figures/}{../hdphmm/supporting_figures/}}
 
@@
 
-%\input structure.tex
+\input structure.tex
 %\input structure_si.tex
 
-%\input transport.tex
+\input transport.tex
 %\input transport_si.tex
 
-%\input stochastic_transport.tex
+\input stochastic_transport.tex
+
+\input hdphmm.tex
 
@@
 \appendix
-%\input structure_si.tex
-%\input transport_si.tex
-%\input stochastic_transport_si.tex
+\input structure_si.tex
+\input transport_si.tex
+\input stochastic_transport_si.tex
+\input hdphmm_si.tex
 

### 2020-04-13 Ben_Manuscripts/thesis/transport.tex
Added missing intro figs

@@
   1 $\mu$s MD simulations using 
-  Equation~\ref{eqn:tamsd}:
+  Equation~\ref{eqn:ta_msd}:
   \begin{equation}
 	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
-	\label{eqn:tamsd}
+	\label{eqn:ta_msd}
   \end{equation}
   where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
-  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
+  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form1}:
   \begin{equation} 
 	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
-	\label{eqn:msd_form}
+	\label{eqn:msd_form1}
   \end{equation} 
@@
   Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
-  }\label{fig:msds}
+  }\label{fig:msds2}
   \end{figure}
@@
   probably due to its relatively small size. This likely contributes to the somewhat
-  large error bars on its MSD in Figure~\ref{fig:msds}.
+  large error bars on its MSD in Figure~\ref{fig:msds2}.
 
@@
   DMSO has a comparable MSD to acetone even though it is a larger molecule
-  (see Figure~\ref{fig:msds}). DMSO spends 17\% more time in the pore than acetone. 
+  (see Figure~\ref{fig:msds2}). DMSO spends 17\% more time in the pore than acetone. 
   On average, 35\% of DMSO molecules are coordinated to a sodium ion each

### 2020-04-14 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
Formatted for JPCB with slight mods to intro

--- 2020-02-07 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
@@
-\documentclass[aps,pre,preprint,groupedaddress,longbibliography]{revtex4-2}
+\documentclass[journal=jpcbfk,manuscript=article]{achemso}
 \usepackage{CJK}
@@
 
+\title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling}
+\author{Benjamin J. Coscia}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+\author{Michael R. Shirts}
+\email{michael.shirts@colorado.edu}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+
 \begin{document}
-
-  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
-  with Time Series Modeling}
-
-  \author{Benjamin J. Coscia}
-  \author{Michael R. Shirts}
-
-  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}
-
-  \date{\today}
 
@@
   selectivity. Due to the size of the types of systems we are studying (at
-  least (62,000 atoms) it is prohibitively expensive and time-consuming to run
+  least 62,000 atoms) it is prohibitively expensive and time-consuming to run
   simulations longer than those performed for this work ($\sim$5 $\mu$s).  Even
@@
 
-  We constructed our first model by applying the existing rigorous theoretical
-  foundation which describes the motion of particles that exhibit non-Brownian,
-  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
-  introduced by fractional calculus are instrumental to this
-  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
-  normally linear diffusion equation to fractional derivative orders, providing
-  descriptions of a much more diverse set of behavior, including subdiffusion,
-  a type of anomalous diffusion exhibited by solutes in this
-  study.~\cite{klages_anomalous_2008}
-
-  Three well-known classes of behavior leading to anomalous subdiffusion are
-  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
-  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
-  motion are frequently used alone or in combination to describe single
-  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
-  is characterized by a distribution of hop lengths and dwell times, where
-  trajectories consist of sequential independent random draws from each
-  distribution.\cite{montroll_random_1965} FBM is common in crowded,
-  viscoelastic environments where each jump comes from a Gaussian distribution
-  but is anti-correlated to its previous
-  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
-  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
-  dead ends cause anti-correlated
-  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
-
-  We treated our system as an FBM process subordinate to a CTRW, or
-  subordinated FBM (sFBM) for short. We fit sFBM models in two ways: First, we
-  parameterized solute motion using a single set of parameters fit to a
-  hypothesized anomalous diffusion (AD) model. Second, we used a two-state approach
-  by extracting two sets of model parameters calculated based on a solute's
-  radial distance from the closest pore center. This allows us to include
-  the different dynamical behavior of solutes previously observed within the
-  pore region versus within the monomer tails.
+  % BJC: I'd say this is where the intro starts to get technical
+%  We constructed our first model by applying the existing rigorous theoretical
+%  foundation which describes the motion of particles that exhibit non-Brownian,
+%  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
+%  introduced by fractional calculus are instrumental to this
+%  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
+%  normally linear diffusion equation to fractional derivative orders, providing
+%  descriptions of a much more diverse set of behavior, including subdiffusion,
+%  a type of anomalous diffusion exhibited by solutes in this
+%  study.~\cite{klages_anomalous_2008}
+
+  %BJC: replacement to above.
+  We constructed our first model in order to characterize the hopping and
+  trapping behavior displayed by solutes in our MD simulations. This type 
+  of non-Brownian dynamical behavior results in subdiffusive transport which
+  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
+
+  % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
+  % stole thesis from paragraph below it
+  We chose to treat our system in terms of two well-known classes of anomalous
+  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
+  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
+  FBM is common in crowded, viscoelastic environments where each jump comes 
+  from a Gaussian distribution but is anti-correlated to its previous steps.
+  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
+  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
+  where trajectories consist of sequential independent random draws from each
+  distribution.~\cite{montroll_random_1965} If the draws are not independent,
+  then the hop sequence generation process can be described as subordinate to
+  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
+  suggesting an FBM process is subordinate to the CTRW.
+
+%  Three well-known classes of behavior leading to anomalous subdiffusion are
+%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
+%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
+%  motion are frequently used alone or in combination to describe single
+%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
+%  is characterized by a distribution of hop lengths and dwell times, where
+%  trajectories consist of sequential independent random draws from each
+%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
+%  viscoelastic environments where each jump comes from a Gaussian distribution
+%  but is anti-correlated to its previous
+%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
+%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
+%  dead ends cause anti-correlated
+%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
+
+%  We treated our system as an FBM process subordinate to a CTRW, or
+%  subordinated FBM (sFBM) for short. 
+  We fit sFBM models in two ways: First, we parameterized solute motion using
+  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
+  Second, we used a two-state approach by extracting two sets of model parameters
+  calculated based on a solute's radial distance from the closest pore center. 
+  This allows us to include the different dynamical behavior of solutes previously
+  observed within the pore region versus within the monomer tails.
 
@@
   capacity. Even if a model fails to reproduce the MD MSDs, there is value in
-  uncovering the cause of the deviation. 
-  %BJC9: I modified the following from the commented out version below it in order to be more consistent with what we actually did.
-  The second measure of success is based on the qualitative comparison between
-  individual realizations of solute trajectories generated by our models and
-  those observed from MD simulations. Even if we can reproduce the solute MSDs
-  based on realizations of our models, the absence or inappropriate
-  reproduction of hopping and trapping behavior may indicate underlying model
-  issues. 
-  %The second measure of success is by
-  %analysis of the parameters defining each model. The parameters themselves
-  %should provide clues that help explain solute dynamics in a coherent way. A
-  %model that successfully reproduces MD MSDs, but with nonsensical parameters
-  %has severely diminished value as it could be a consequence of over-fitting.
+  uncovering the cause of the deviation. The second measure of success is based
+  on the qualitative comparison between individual realizations of solute 
+  trajectories generated by our models and those observed from MD simulations. 
+  Even if we can reproduce the solute MSDs based on realizations of our models,
+  the absence or inappropriate reproduction of hopping and trapping behavior may
+  indicate underlying model issues.
 
@@
   We performed all post-simulation trajectory analysis using Python scripts
-  which are available online at \\
+  which are available online at
   \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.  The appropriate
@@
   in our analysis of solute kinetics. We plot the solute partition versus time in
-  Figure~\ref{S-fig:equilibration} of the Supplemental Material in order to justify
+  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify
   our choice of equilibration times for each solute.
@@
   Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
-  Figure~\ref{S-fig:hurst_autocorrelation} of the Supplemental Material). Any hope of
+  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
   fitting longer time lags to our data is lost in the noise since the analytical values
@@
   from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
-  See Section~\ref{S-section:H_estimate} of the Supplemental Material for numerical
+  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
   simulations illustrating this point.
@@
   and our own Python implementation (see Table~\ref{S-table:python_scripts} of
-  the Supplemental Material) of the algorithm by Stoev and Taqqu to
+  the Supporting Information) of the algorithm by Stoev and Taqqu to
   simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
@@
   correction to enhance the accuracy of the correlation structure (see
-  Section~\ref{S-section:flm_correlation} of the Supplemental Material for
+  Section~\ref{S-section:flm_correlation} of the Supporting Information for
   validation of the approach).
@@
   verified the Markovianity of state transitions as described in
-  Section~\ref{S-section:markov_validation} of the Supplemental Material.
+  Section~\ref{S-section:markov_validation} of the Supporting Information.
 
@@
   Equation~\ref{eqn:passage_times} is given in
-  Section~\ref{S-section:fpt_derivation} of the Supplemental Material. We
+  Section~\ref{S-section:fpt_derivation} of the Supporting Information. We
   calculated the expected value of Equation~\ref{eqn:passage_times} in order to
@@
 	  show similar distributions and autocorrelation functions (see
-	  Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
+	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
   }\label{fig:anticorrelated_hops}
@@
   shapes of urea and acetic acid's MSD curves are also very similar (see
-  Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).
+  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
 
@@
   measured from MD simulations within or near statistical uncertainty. In
-  Figure~\ref{S-fig:train_test} of the Supplemental Material, we parameterized
+  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized
   the AD models using the first half of the stationary solute equilibrated
@@
   parameters are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated
-  in the Supplemental Material, Table~\ref{S-table:msddm_params}).
+  in the Supporting Information, Table~\ref{S-table:msddm_params}).
 
@@
 	  similar fits for the remaining solutes in
-	  Figure~\ref{S-fig:ad_fpt_fits} of the Supplemental Material. (b) The
+	  Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The
 	  single particle flux measured by the sFBMcut AD model decays with
@@
 
-  \section*{Supplemental Material}
+  \section*{Supporting Information}
 
   Detailed explanations and expansions upon the results and procedures
-  mentioned in the main text are described in the Supplemental Material. This
+  mentioned in the main text are described in the Supporting Information. This
   information is available free of charge via the Internet at

### 2020-04-14 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
Minor additional comments
Update draft.

@@
   set of solutes over much longer timescales.
-
+  %MRS11: Maybe this last sentence could be changed. Because you aren't really finding a way to study larger sets of 
+  %solutes over larger timescales, you are using a limited amount of atomistic simulation into long time scale behavior efficiently. We can discuss variations as needed!
+
+  %BJC: maybe this paragraph can be cut down?
   Mathematical descriptions of transport in complex separations membranes are a
@@
   \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
+  %MRS11: this next sentence could probably be cut - it's kind of vague.
   The complexity of a well-fit model generally parallels the complexity of the
   transport mechanism being studied, as well as the transport information the
-  model conveys. In dense homogeneous membranes, the solution-diffusion model
+  model conveys. 
+  In dense homogeneous membranes, the solution-diffusion model
   can extract diffusion and partition coefficients and has successfully
@@
 
+  %MRS11: in this paragraph, the ``we can'' is vague, and doesn't
+  %abscribe agency.  Is ``We'' our group? Is it the field as whole?
+  %If it's something someone has done in the past, there should be
+  %citations. If it's something that can be done in the future, the
+  %phrasing should be a long the lines of ``it is possible to'', ``it
+  %can be done'', etc.
+
   Using a bottom-up modeling approach, we can parameterize single particle
@@
 
+  %MRS11: should be clear if first model is previous publications, or what is presented here.
+  %If what is presented here, should talk about how it will be presented, not that it was developed. 
+  %MRS11: research activities happened in the past, presentation of research is described in the present.
+  %or potentially future if describing what will be presented in the rest of the paper. 
   %BJC: replacement to above.
@@
   functionality and experience each of the three trapping mechanisms to different extents.
+
+  %MRS11: Introduction should not really give the answer so far.
+  %Introduction should describe the questions that will bbe asked, but
+  %not answer them.  That's not what is expected in an intro, it may confuse people (answers should be in the abstract).
+  %MRS11: this next paragraph could use tweaks/cutting the most, but review the previous paragraphs as well.
+  %MRS11: you can think about putting some of these results into conclusion, though - it reads well now, but might be benefitted from reemphasizing results if it's currently missing any of this.
 
@@
   %if one makes enough assumptions about what the functional form of the distribution is. And we could
-  %presumaly come up with something reasonable. But that's for another time. 
+  %presumably come up with something reasonable. But that's for another time. 
   correlate emissions coming from different hop distributions. Many
@@
 % LocalWords:  timestep pre selectivtiy foulants subfigures RWFs roman github
-% LocalWords:  al linkable nanopores
+% LocalWords:  al linkable nanopores klages

### 2020-04-15 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
Modifications based on MRS comments

@@
   trajectories per unit cell in order to minimize solute-solute interactions.
-  This results in relatively high uncertainties in observables such as mean
-  squared displacement (MSD), preventing reliable long timescale predictions.
-  We are in need of a way of studying the collective motion of a much larger
-  set of solutes over much longer timescales.
+% BJC2: removed this sentence. High uncertainty MSDs don't really relate to long timescale predictions. Unless the MSDs were linear.
+%  This results in relatively high uncertainties in observables such as mean
+%  squared displacement (MSD), preventing reliable long timescale predictions.
+  We are in need of an efficient method which can use our limited atomistic 
+  simulation data sets in order to predict long timescale solute behavior.  
+  %BJC2: following sentence replaced with above
+%  We are in need of a way of studying the collective motion of a much larger
+%  set of solutes over much longer timescales.
   %MRS11: Maybe this last sentence could be changed. Because you aren't really finding a way to study larger sets of 
@@
   %MRS11: this next sentence could probably be cut - it's kind of vague.
-  The complexity of a well-fit model generally parallels the complexity of the
-  transport mechanism being studied, as well as the transport information the
-  model conveys. 
+  %BJC2: True
+%  The complexity of a well-fit model generally parallels the complexity of the
+%  transport mechanism being studied, as well as the transport information the
+%  model conveys. 
   In dense homogeneous membranes, the solution-diffusion model
@@
 
-  Using a bottom-up modeling approach, we can parameterize single particle
-  behavior by extracting particle trajectories from MD simulations and studying
-  the properties that have the greatest influence on solute dynamics. With this
-  information, we can learn how to construct an ensemble of characteristic
+  Using a bottom-up modeling approach, it may be possible to parameterize single
+  particle behavior by extracting particle trajectories from MD simulations and
+  studying the properties that have the greatest influence on solute dynamics.
+  With this information, one can learn how to construct an ensemble of characteristic
   single solute trajectories with these properties which would be useful for
@@
   uncertainties. Fortunately, there is an abundance of information encoded in
-  the complex solute trajectories. We can incorporate fluctuations and 
+  the complex solute trajectories. One can incorporate fluctuations and 
   time-dependent correlations in solute position into transport models, 
-  as well as the length of time solutes are trapped. We can add further detail by integrating
-  this time series analysis with our knowledge of the primary trapping
-  mechanisms as well as the solute's changing chemical environment within the
-  heterogeneous membrane.
+  as well as the length of time solutes are trapped. It is possible to add further
+  detail by integrating this time series analysis with existing knowledge of the
+  primary trapping mechanisms as well as the solute's changing chemical environment
+  within the heterogeneous membrane.
 
@@
   %BJC: replacement to above.
-  We constructed our first model in order to characterize the hopping and
-  trapping behavior displayed by solutes in our MD simulations. This type 
-  of non-Brownian dynamical behavior results in subdiffusive transport which
+  %BJC1: Made clear that this is talking about the first model of this work.
+  %BJC1: went through rest of intro to make sure tense is consistent
+  The first model that we develop in this work, allows us to characterize the 
+  hopping and trapping behavior displayed by solutes in our MD simulations. This 
+  type of non-Brownian dynamical behavior results in subdiffusive transport which
   is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
@@
   % stole thesis from paragraph below it
-  We chose to treat our system in terms of two well-known classes of anomalous
+  We treat our system in terms of two well-known classes of anomalous
   subdiffusion: fractional Brownian motion (FBM) subordinate to a 
@@
 %  subordinated FBM (sFBM) for short. 
-  We fit sFBM models in two ways: First, we parameterized solute motion using
+  We fit sFBM models in two ways: First, we parameterize solute motion using
   a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
-  Second, we used a two-state approach by extracting two sets of model parameters
+  Second, we use a two-state approach by extracting two sets of model parameters
   calculated based on a solute's radial distance from the closest pore center. 
@@
   those states.~\cite{bowman_using_2009} We extend the framework to include
-  state-dependent fluctuations and correlations in solute position. The
-  magnitude of a solute's fluctuations from its average trapped position and the
-  degree of correlation with previous fluctuations is determined by the current
+  state-dependent fluctuations and correlations in solute position. The model
+  determines the magnitude of a solute's fluctuations from its average trapped
+  position and the degree of correlation with previous fluctuations by its current
   state. To distinguish our approach from standard MSMs, we have named it the
@@
   %MRS11: you can think about putting some of these results into conclusion, though - it reads well now, but might be benefitted from reemphasizing results if it's currently missing any of this.
-
-  Finally, we use both models in order to predict solute flux and selectivity
-  in pores of macroscopic length, thus achieving a better understanding of
-  macroscopic properties on the basis of microscopic dynamics. We show that
-  anti-correlated solute hopping behavior severely reduces flux relative to
-  uncorrelated behavior. We use the relative solute fluxes to estimate the
-  membrane's selectivity between all pairs of solutes and demonstrate that,
-  when solutes display different degrees of anti-correlated hopping behavior,
-  selectivity becomes a function of pore length. With this improved
-  understanding of macroscopic behavior, we can begin to think more critically
-  about how to design membranes in order to selectively pass or reject specific
-  solutes.
+  %BJC2: slight tweaks and removed conclusions from following paragraph. Also went back through previous
+  % paragraphs to look for conclusions.
+
+  Finally, we demonstrate how one can use stochastically generated realizations
+  of our models in order to predict solute flux and selectivity in pores of 
+  macroscopic length, thus achieving a better understanding of macroscopic 
+  properties on the basis of microscopic dynamics. By improving our 
+  understanding of macroscopic behavior in this way, we can begin to think more
+  critically about how to design membranes in order to selectively pass or 
+  reject specific solutes.
 

### 2020-04-16 Ben_Manuscripts/stochastic_transport/arxiv/ms.tex
formatted for arXiv

--- 2020-04-15 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
@@
-\documentclass[journal=jpcbfk,manuscript=article]{achemso}
+\documentclass[aps,pre,twocolumn,showpacs,preprintnumbers,amsmath,amssymb,footinbib]{revtex4-2}
 \usepackage{CJK}
@@
 
-\title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling}
+\begin{document}
+
+  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+  with Time Series Modeling}
+
   \author{Benjamin J. Coscia}
-\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
   \author{Michael R. Shirts}
-\email{michael.shirts@colorado.edu}
-\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
-
-\begin{document}
+
+  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}
+
+  \date{\today}
 
@@
   %MRS11: in this paragraph, the ``we can'' is vague, and doesn't
-  %abscribe agency.  Is ``We'' our group? Is it the field as whole?
+  %ascribe agency.  Is ``We'' our group? Is it the field as whole?
   %If it's something someone has done in the past, there should be
@@
   %BJC1: went through rest of intro to make sure tense is consistent
-  The first model that we develop in this work, allows us to characterize the 
+  The first model that we develop in this work allows us to characterize the 
   hopping and trapping behavior displayed by solutes in our MD simulations. This 
@@
   is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
-
+  %MRS12: removing paragraph break
   % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
@@
   %MRS11: Introduction should not really give the answer so far.
-  %Introduction should describe the questions that will bbe asked, but
+  %Introduction should describe the questions that will be asked, but
   %not answer them.  That's not what is expected in an intro, it may confuse people (answers should be in the abstract).
   %MRS11: this next paragraph could use tweaks/cutting the most, but review the previous paragraphs as well.
-  %MRS11: you can think about putting some of these results into conclusion, though - it reads well now, but might be benefitted from reemphasizing results if it's currently missing any of this.
+  %MRS11: you can think about putting some of these results into conclusion, though - it reads well now, but might be benefited from reemphasizing results if it's currently missing any of this.
   %BJC2: slight tweaks and removed conclusions from following paragraph. Also went back through previous
@@
 
-  \begin{figure}
+  \begin{figure*}
   \centering
@@
   the tail region are omitted for clarity.}\label{fig:membrane_structure}
-  \end{figure}
+  \end{figure*}
 
@@
   \begin{equation}
-    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
+  	\begin{split}
+    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) \\
+    -\alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
+    \end{split}
   \label{eqn:powerlaw_cutoff_likelihood}
@@
   \begin{equation}
-    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
+  \begin{split}
+    p_{\alpha_h, \beta}(k;\mu,\sigma) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
+    \exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
+  \end{split}
   \end{equation}
@@
   \begin{equation}
-    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
+  \begin{gathered}
+    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg], \\
     ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
+  \end{gathered}
   \label{eqn:flm_autocovariance}
@@
 %MRS9: I'd go with what they said.  Looking at PRE, it looks like you can put double lines above and below the table, though - I added them 
-  \begin{table}[!htb]
+  \begin{table*}[!htb]
 	  \centering
@@
 
- \end{table}
+ \end{table*}
 
@@
 
-  \begin{table}[!htb]
+  \begin{table*}[!htb]
 	  \centering
@@
 	  trapping mechanisms.}\label{table:states}  
-  \end{table}
+  \end{table*}
 
@@
   \begin{equation}
-  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
+  \begin{split}
+  P(t) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
+  -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
+  \end{split}
   \label{eqn:passage_times}
@@
   }\label{fig:solute_trajectories}
-  \end{figure}
-
-  \begin{figure}
+  \end{figure*}
+
+  \begin{figure*}
   \centering
@@
   }\label{fig:anticorrelated_hops}
-  \end{figure}
+  \end{figure*}
 
@@
   }\label{fig:ad_eyetest}
-  \end{figure}
+  \end{figure*}
 
@@
   }\label{fig:anomalous_msds}
-  \end{figure}
-
-  \begin{figure}
+  \end{figure*}
+
+  \begin{figure*}
   \centering
@@
 	  behavior closer to the Brownian limit.}\label{fig:1mode_parameters}
-  \end{figure}
-
-  \begin{figure}
+  \end{figure*}
+
+  \begin{figure*}
   \centering
@@
   }\label{fig:2mode_parameters}
-  \end{figure}
+  \end{figure*}
 
@@
 	  \label{fig:msddm_emissions}
-  \end{figure}
-
-  \begin{figure}
+  \end{figure*}
+
+  \begin{figure*}
   \centering
@@
 	  heaviest tails.}\label{fig:msddm_parameters}
-  \end{figure}
+  \end{figure*}
 
@@
 	  }\label{fig:msddm_performance}
-  \end{figure}
+  \end{figure*}
 
@@
   	  }\label{fig:msddm_eyetest}
-  \end{figure}
+  \end{figure*}
 
@@
   }\label{fig:flux_curves}
-  \end{figure}
+  \end{figure*}
 
@@
  	  }\label{fig:beta}
-  \end{figure}
+  \end{figure*}
 

### 2020-04-17 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
Tweaks.
Cover letter for JPCB

@@
 
+\usepackage[utf8]{inputenc}
 \DeclareUnicodeCharacter{03C9}{$\omega$}
@@
 
-  \graphicspath{{./figures/}}
+  \graphicspath{{./figures/arxiv_figures/}}
 
@@
   scripts to use for subsequent calculations are summarized in
-  Table~\ref{S-table:python_scripts} of the Supplemental Material.
+  Table~\ref{S-table:python_scripts} of the Supporting Information.
 
@@
   to deviate from the empirically measured PDF (see
-  Section~\ref{S-section:truncation} of the Supplemental
-  Material).~\cite{mantegna_stochastic_1994}
+  Section~\ref{S-section:truncation} of the Supporting Information).~\cite{mantegna_stochastic_1994}
 
@@
 
-  We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
+  We used the Python package \texttt{fbm}~\cite{flynn_exact_2019} to generate exact simulations of FBM
   and our own Python implementation (see Table~\ref{S-table:python_scripts} of
@@
   Predictions made with these models consistently under-predict the MD MSDs
-  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supplemental
-  Material). Therefore, we will not include the pure sFBM or sFLM models in the
+  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supporting Information).
+  Therefore, we will not include the pure sFBM or sFLM models in the
   remainder of our analysis.
@@
   longer. One could improve performance significantly by simulating less
-  trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supplemental
-  Material, we determined that one can simulate as few as 100 sFBMcut
+  trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting
+  Information, we determined that one can simulate as few as 100 sFBMcut
   realizations in order to parameterize Equation~\ref{eqn:flux_decay}. For
@@
   % No TOC image in PRE
-  %\section*{TOC Graphic}
-
-  %\begin{figure}[!htb]
-  %\centering
-  %\includegraphics[width=3.25in]{toc.pdf}
-  %\end{figure}
+  \section*{TOC Graphic}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=3.25in]{toc.pdf}
+  \end{figure}
 

### 2020-04-17 Ben_Manuscripts/stochastic_transport/arxiv/ms.tex
Cover letter for JPCB

@@
-\documentclass[aps,pre,twocolumn,showpacs,preprintnumbers,amsmath,amssymb,footinbib]{revtex4-2}
-\usepackage{CJK}
+%\documentclass[aps,pre,twocolumn,showpacs,preprintnumbers,amsmath,amssymb,footinbib]{revtex4-1}
+\documentclass[journal=ancac3,manuscript=article,layout=twocolumn]{achemso}
+%\usepackage{CJK}
+
+\let\titlefont\undefined
+\makeatletter
+\let\l@addto@macro\relax
+\makeatother
+\usepackage[fontsize=10pt]{scrextend}
 
@@
 \usepackage{subcaption}
-%\usepackage{caption}
+%\usepackage[caption=false]{subfig}
 \usepackage{amsmath} % or simply amstext
@@
 \usepackage{float}
-\usepackage{xr}
 \usepackage{diagbox}
 \usepackage{array}
+
+\SectionNumbersOn
 
@@
 
-\externaldocument[S-]{Supporting_Information}
+\title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling}
+\author{Benjamin J. Coscia}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+\author{Michael R. Shirts}
+\email{michael.shirts@colorado.edu}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
 
@@
 
-  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
-  with Time Series Modeling}
-
-  \author{Benjamin J. Coscia}
-  \author{Michael R. Shirts}
-
-  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}
-
-  \date{\today}
+%  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+%  with Time Series Modeling}
+%  
+%  \author{Benjamin J. Coscia}
+%  \author{Michael R. Shirts}
+%  
+%  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}
+%
+%  \date{\today}
 
@@
 
-  \graphicspath{{./figures/}}
+  \graphicspath{{./figures/arxiv_figures/}{./supporting_figures/arxiv_figures/}}
 
@@
   scripts to use for subsequent calculations are summarized in
-  Table~\ref{S-table:python_scripts} of the Supplemental Material.
+  Table~\ref{table:python_scripts} of the Supporting Information.
 
@@
   \end{figure*}
+
+%  \begin{figure*}
+%  \centering
+%  \subfloat[\label{fig:monomer_structure}]{%
+%  \vspace{1.1cm}
+%  \includegraphics[width=0.4\textwidth]{NaGA3C11.pdf}%
+%  \vspace{0.6cm}
+%  }\hfill
+%  \subfloat[\label{fig:membrane_profile}]{%
+%    \includegraphics[width=\textwidth]{membrane_profile.pdf}%
+%  }\hfill
+%  \caption{}\label{fig:membrane_profile}
+%  \end{subfigure}
+%  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
+%  hexagonal phase in the presence of water where the carboxylate head groups occupy the
+%  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
+%  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
+%  straight and uniform sized pores. Water molecules (red and white spheres) present in 
+%  the tail region are omitted for clarity.}\label{fig:membrane_structure}
+%  \end{figure*}
 
@@
   in our analysis of solute kinetics. We plot the solute partition versus time in
-  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify
+  Figure~\ref{fig:equilibration} of the Supporting Information in order to justify
   our choice of equilibration times for each solute.
@@
   Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
-  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
+  Figure~\ref{fig:hurst_autocorrelation} of the Supporting Information). Any hope of
   fitting longer time lags to our data is lost in the noise since the analytical values
@@
   from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
-  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
+  See Section~\ref{section:H_estimate} of the Supporting Information for numerical
   simulations illustrating this point.
@@
   to deviate from the empirically measured PDF (see
-  Section~\ref{S-section:truncation} of the Supplemental
-  Material).~\cite{mantegna_stochastic_1994}
+  Section~\ref{section:truncation} of the Supporting Information).~\cite{mantegna_stochastic_1994}
 
@@
 
-  We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
-  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
+  We used the Python package \texttt{fbm}~\cite{flynn_exact_2019} to generate exact simulations of FBM
+  and our own Python implementation (see Table~\ref{table:python_scripts} of
   the Supporting Information) of the algorithm by Stoev and Taqqu to
@@
   correction to enhance the accuracy of the correlation structure (see
-  Section~\ref{S-section:flm_correlation} of the Supporting Information for
+  Section~\ref{section:flm_correlation} of the Supporting Information for
   validation of the approach).
@@
   verified the Markovianity of state transitions as described in
-  Section~\ref{S-section:markov_validation} of the Supporting Information.
+  Section~\ref{section:markov_validation} of the Supporting Information.
 
@@
   Equation~\ref{eqn:passage_times} is given in
-  Section~\ref{S-section:fpt_derivation} of the Supporting Information. We
+  Section~\ref{section:fpt_derivation} of the Supporting Information. We
   calculated the expected value of Equation~\ref{eqn:passage_times} in order to
@@
 	  show similar distributions and autocorrelation functions (see
-	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
+	  Figure~\ref{fig:anticorrelated_hops} of the Supporting Information).
   }\label{fig:anticorrelated_hops}
@@
   Predictions made with these models consistently under-predict the MD MSDs
-  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supplemental
-  Material). Therefore, we will not include the pure sFBM or sFLM models in the
+  (see Figure~\ref{fig:anomalous_msds_bothmode} of the Supporting Information).
+  Therefore, we will not include the pure sFBM or sFLM models in the
   remainder of our analysis.
@@
   number of solutes inside the pores and tails stabilized
-  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
+  (Figure~\ref{fig:equilibration}).  With this definition, we observe
   evidence of non-stationary solute behavior after the perceived equilibration
@@
   shapes of urea and acetic acid's MSD curves are also very similar (see
-  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
+  Figure~\ref{fig:msd_comparison} of the Supporting Information).
 
@@
   measured from MD simulations within or near statistical uncertainty. In
-  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized
+  Figure~\ref{fig:train_test} of the Supporting Information, we parameterized
   the AD models using the first half of the stationary solute equilibrated
@@
   parameters are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated
-  in the Supporting Information, Table~\ref{S-table:msddm_params}).
+  in the Supporting Information, Table~\ref{table:msddm_params}).
 
@@
   longer. One could improve performance significantly by simulating less
-  trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supplemental
-  Material, we determined that one can simulate as few as 100 sFBMcut
+  trajectories. In Figure~\ref{fig:flux_curve_sensitivity} of the Supporting Information,
+  we determined that one can simulate as few as 100 sFBMcut
   realizations in order to parameterize Equation~\ref{eqn:flux_decay}. For
@@
 	  similar fits for the remaining solutes in
-	  Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The
+	  Figure~\ref{fig:ad_fpt_fits} of the Supporting Information. (b) The
 	  single particle flux measured by the sFBMcut AD model decays with
@@
 
-  \section*{Supporting Information}
-
-  Detailed explanations and expansions upon the results and procedures
-  mentioned in the main text are described in the Supporting Information. This
-  information is available free of charge via the Internet at
-  http://pubs.acs.org.
+%  \section*{Supporting Information}
+%
+%  Detailed explanations and expansions upon the results and procedures
+%  mentioned in the main text are described in the Supporting Information. This
+%  information is available free of charge via the Internet at
+%  http://pubs.acs.org.
 
@@
 
+  \section*{Supporting Information}
+
+  \input si_arxiv.tex
+
+  \clearpage
   %\bibliographystyle{apsrev4-2}

### 2020-04-17 Ben_Manuscripts/stochastic_transport/cover_letter_JPCB.tex
Cover letter for JPCB

--- 2020-02-07 Ben_Manuscripts/stochastic_transport/cover_letter.tex
@@
 	%\noindent May 3\textsuperscript{rd}, 2019\\
-	\noindent \date
+	\noindent \today \\
 
@@
 	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael R.
-	Shirts, for	consideration for publication as a Research Article in Physical 
-	Review E. We expect this work to be of significant interest to researchers 
-	who study complex dynamics in both structured and amorphous soft materials.
+	Shirts, for	consideration for publication as an Article in the Journal of 
+	Physical Chemistry B. We expect this work to be of significant interest to 
+	researchers who study complex transport in both structured and amorphous 
+	soft materials. Please note that this article has been upload to arXiv with
+	differences only in formatting.  % BJC: probably should include link (once I have one)?
 
 	In this article, we use solute trajectories generated from 5$\mu$s molecular
-	dynamics (MD) simulations of an inverted hexagonal (H\textsubsript{II}) phase
+	dynamics (MD) simulations of an inverted hexagonal (H\textsubscript{II}) phase
 	self-assembled lyotropic liquid crystal (LLC) polymer membrane in order to 
@@
 	%BJC: included phone numbers because it asked to do so in author's guide.
+	%BJC: Should I just narrow down to three suggestions?
 	\noindent Some suggestions for reviewers are:
@@
 
-		\item Menachem Elimelech is a leader in the development of membrane technologies
-		for	water desalination and water reuse (Yale University, 203-432-2789,
-		\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).
-
 		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
-		and various	nanostructured materials (Northeastern University, 617-373-8619 	
-		\href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})
+		and transport under confinement within various nanostructured materials 
+		(Northeastern University, 617-373-8619,\\ \href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})
 
@@
 		including work on ion transport in various ordered liquid crystalline phases. 
-		(University of Minnesota, 612-625-4599,\href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})
+		(University of Minnesota, 612-625-4599, \href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})
+
+		%BJC: Maybe not klafter because he hasn't published since 2015. It looks like he has been president of his university
+		\item Joseph Klafter is an expert in anomalous diffusion theory, particularly with that 
+		relevant to our work. (Tel Aviv University, 03-6406106, \href{mailto:klafter@tauex.tau.ac.il}{klafter@tauex.tau.ac.il})
+
+		\item Stephen Paddison uses various levels of molecular simulation theory to understand
+		proton transport in nanostructured and charged polymer membranes. (The University of Tennessee 
+		Knoxville, 865-974-2026, \href{mailto:spaddison@utk.edu}{spaddison@utk.edu})
 

### 2020-04-17 Ben_Manuscripts/stochastic_transport/ms.tex
Cover letter for JPCB

--- 2020-04-17 Ben_Manuscripts/stochastic_transport/arxiv/ms.tex
@@
   Predictions made with these models consistently under-predict the MD MSDs
-  (see Figure~\ref{fig:anomalous_msds_bothmode} of the Supporting Information).
+  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supporting Information).
   Therefore, we will not include the pure sFBM or sFLM models in the

### 2020-04-17 Ben_Manuscripts/stochastic_transport/cover_letter_JPCB.tex
Add comments.

@@
 	researchers who study complex transport in both structured and amorphous 
-	soft materials. Please note that this article has been upload to arXiv with
+	soft materials. Please note that this article has been uploaded to arXiv with
 	differences only in formatting.  % BJC: probably should include link (once I have one)?
@@
 	solutes in MD simulations. This is among the first studies to apply time 
-	series modeling approaches in order to predict bulk materials properties.
+	series modeling of molecular simulations in order to predict bulk materials properties.
 
-	Recently, we characterized transport mechanisms exhibited by a series of 
+	This article builds on recent work of ours also published in J. Phys. Chem. B 
+        where we characterized transport mechanisms exhibited by a series of 
 	small polar solutes in an LLC Membrane (Coscia and Shirts \textit{J. Phys.
-	Chem. B}, 123, 6314--6330 (2019)). We observed subdiffusive solute transport
+	Chem. B}, 123, 6314--6330 (2019)). In that study, we observed subdiffusive solute transport
 	characterized by intermittent hops separated by periods of entrapment. In
@@
 	anomalous diffusion literature, we parameterize solute motion as 
-    subordinated fractional Brownian and L\'evy motion processes. This implies that 
+    subordinated fractional Brownian and L\'evy motion processes, based on the observation that 
 	solutes experience a series of dwell times separated by anti-correlated hop
@@
 	%BJC: Should I just narrow down to three suggestions?
+        %MRS: more is fine, but yes, if Klafter is univeristy president, pointless to include. Looking, it 
+        %     looks like he finished as president last year, but probably not getting back to research soon.
+        %     A review from JPCB woould be low on his priority list.
 	\noindent Some suggestions for reviewers are:
@@
 		%BJC: Maybe not klafter because he hasn't published since 2015. It looks like he has been president of his university
+                %MRS: yes, see above.
 		\item Joseph Klafter is an expert in anomalous diffusion theory, particularly with that 
@@
 
-% LocalWords:  BJC
+% LocalWords:  BJC Subdiffusive Solute Nanoscale Coscia arXiv solute lyotropic
+% LocalWords:  LLC MSDs solutes Phys Chem subdiffusive evy timescales Klafter
+% LocalWords:  univeristy JPCB woould nanostructured Mahesh Mahanthappa klafter
+% LocalWords:  Tel Paddison

### 2020-04-27 Ben_Manuscripts/stochastic_transport/cover_letter_JPCB.tex
spell checking and mod to usage of subdiffusion

@@
 	soft materials. Please note that this article has been uploaded to arXiv with
-	differences only in formatting.  % BJC: probably should include link (once I have one)?
+	differences only in formatting: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\
 
@@
 	solutes in MD simulations. This is among the first studies to apply time 
-	series modeling of molecular simulations in order to predict bulk materials properties.
+	series modeling of molecular simulations in order to predict bulk materials properties.\\
 
@@
 	Finally, we demonstrate how one can project our best model onto macroscopic 
-	timescales in order to estimate solute flux and selectivity.
+	timescales in order to estimate solute flux and selectivity.\\
 
 	%BJC: included phone numbers because it asked to do so in author's guide.
-	%BJC: Should I just narrow down to three suggestions?
-        %MRS: more is fine, but yes, if Klafter is univeristy president, pointless to include. Looking, it 
-        %     looks like he finished as president last year, but probably not getting back to research soon.
-        %     A review from JPCB woould be low on his priority list.
 	\noindent Some suggestions for reviewers are:
@@
 		(University of Minnesota, 612-625-4599, \href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})
-
-		%BJC: Maybe not klafter because he hasn't published since 2015. It looks like he has been president of his university
-                %MRS: yes, see above.
-		\item Joseph Klafter is an expert in anomalous diffusion theory, particularly with that 
-		relevant to our work. (Tel Aviv University, 03-6406106, \href{mailto:klafter@tauex.tau.ac.il}{klafter@tauex.tau.ac.il})
 

### 2020-04-27 Ben_Manuscripts/thesis/hdphmm.tex
spell checking and mod to usage of subdiffusion

--- 2020-04-13 Ben_Manuscripts/hdphmm/Draft.tex
@@
-\documentclass{article}
-
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
-\usepackage{amssymb}
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\newcommand{\colormap}{jet}  % colorbar to use
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\usepackage{xr}
-\usepackage{setspace}
-\doublespacing
-%\DeclareUnicodeCharacter{03C9}{$\omega$}
-\externaldocument[S-]{Supporting_Information}
-
-\title{Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
-       of Solute Trajectories in Nanostructured Membranes.}
-
-\author{Benjamin J. Coscia, Christopher P. Calderon, Michael R. Shirts}
-
-\begin{document}
-
-  \graphicspath{{./figures/}}
-  \maketitle
+\chapter{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+  with Time Series Modeling}
 
   \section{Introduction}
-
-%  There is a need for highly selective membranes in order to perform efficient 
-%  separations of components of complex aqueous streams.
-%  %MRS2: add some more examples (When you get around to it).
-%  \begin{itemize}
-%    \item Organic micropollutants
-%    \item Desalination and boric acid removal from seawater.
-%    \item While many researchers focus on membrane permeability, we may be 
-%    able to reduce costs of commercial nanofiltration and reverse osmosis with
-%    higher selectivity.~\cite{werber_materials_2016}
-%  \end{itemize}
-%
-%%  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.
-%%  \begin{itemize}
-%%    \item 
-%%  \end{itemize}
-%
-%  Lyotropic liquid crystals (LLC) are a class of amphiphilic molecules whose ordered phases
-%  can be cross-linked into mechanically strong membranes capable of highly selective
-%  separations.
-%  \begin{itemize}
-%    \item The shape of the LLC monomers and water content dictates the ordered phase 
-%    that they form. There are two phases of particular interest for membrane applications.
-%  	\item H\textsubscript{II} phase lyotropic liquid crystals are characterized by 
-%  	hexagonally packed, straight, pores while the Q\textsubscript{I} phase consists of
-%  	a tortuous network of 3D interconnected pores. 
-%  	\item In both cases the pores are uniform in size with radii on the order of 1 nm
-%    %MRS2: is it really a molecular weight cutoff?
-%    %BJC2: is molecular size better? Obviously there are other factors like shape, but I don't want to get into that
-%  	giving them a very strict molecular size cut-off.
-%	\item Additionally, they have the potential to disrupt conventional membrane separation
-%	techniques by being selective based not only on size and charge, but on chemical
-%	functionality as well.
-%	\item Their pores are lined with LLC monomer functional groups which can potentially
-%	be designed to interact with solutes in a chemically-specific manner
-%  \end{itemize}
-%
-%  There are limits to what we can learn from experiment about LLC membrane design.
-%  \begin{itemize}
-%    \item Experimental observables like permeability and selectivity allow us to speculate
-%    about the molecular origins of separation processes.
-%    %MRS2: not quite sure what you mean below?
-%    \item This drives an empirical design approach which can potentially neglect key
-%    interactions which influence selectivity.
-%    \item LLC membranes have been shown to exhibit selectivities which cannot be fully 
-%    explained by relatively simple macroscopic models. 
-%  \end{itemize}
-%  
-%  Molecular Dynamics (MD) simulations can give us mechanistic insights with atomistic 
-%  resolution so that we can intelligently design new membranes for solute-specific 
-%  separations.
-%  \begin{itemize}
-%    \item In our previous work, we built a detailed atomistic model which we used
-%    to understand the nanoscopic structure of an LLC Membrane.~\cite{coscia_understanding_2019}
-%    \item We also used the model in order to gain a qualitative understanding of 
-%    trapping mechanisms which lead to subdiffusive transport behavior.~\cite{coscia_chemically_2019}
-%  \end{itemize}
-%
-%  Unfortunately, the timescales that we can simulate with MD are insufficient to be
-%  able to make well-converged predictions of macroscopic transport properties 
-%  traditionally used to characterize membranes in the lab.
-%  \begin{itemize}
-%    %MRS2: would be good to get this next point into the first line of a paragraph, since it's quite important. 
-%    \item However, if we use descriptive stochastic models that can capture solute
-%    dynamics, then we could project long timescale behavior in addition to gaining
-%    a deeper understanding of solute behavior on short timescales.
-%  \end{itemize}
-
-  %%%%%%%%%%%%%%%%%%%%%%%% Thesis chapter starts here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   In this work we attempt to minimize human effort by applying the infinite hidden 
-  Markov Model (IHMM)~\cite{beal_infinite_2002,calderon_inferring_2015}, a nonparameteric 
+  Markov Model (IHMM)~\cite{beal_infinite_2002,calderon_inferring_2015}, a nonparametric 
   Bayesian classification technique, in order to automatically detect and infer the 
@@
   ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}  
-  Our python implementation of the IHMM algorithm is available online at 
+  Our python implementation of the IHMM algorithm is available online at \\
   \texttt{https://github.com/bencoscia/hdphmm}. All other post-simulation 
@@
   the time series of parameter estimates. Plots illustrating parameter convergence are 
-  available in Section~\ref{S-section:convergence} of the Supporting Information. We refer the interested reader to 
+  available in Section~\ref{section:convergence} of Appendix D. We refer the interested reader to 
   much more extensive descriptions of the inference and sampling procedures used to 
@@
   cylinder where we expect solutes to exhibit radially symmetric dynamics. We 
-  present a step-by-step demonstration of our procedure in Section~\ref{S-section:ihmm_procedure}
-  of the Supporting Information.
+  present a step-by-step demonstration of our procedure in Section~\ref{section:ihmm_procedure}
+  of Appendix D.
 
@@
   the Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. 
-  In Section~\ref{S-section:prior_guesses} of the Supporting Information we outline our method for 
+  In Section~\ref{section:prior_guesses} of Appendix D we outline our method for 
   choosing reliable prior parameters. The entries of $A$ and $\Sigma$ do 
@@
   In these cases, the mean in each dimension tends to be a more reliable indicator of
-  convergence (see Figure~\ref{S-fig:convergence3d} of the Supporting Information).
+  convergence (see Figure~\ref{fig:convergence3d} of Appendix D).
 
@@
   equilibration time of all dimensions as the equilibration time point.
-%  Further details are available in Section~\ref{S-section:convergence} of
-%  the Supporting Information.
+%  Further details are available in Section~\ref{section:convergence} of
+%  Appendix D.
 
@@
   terms of $r$ and $z$. Since we fixed the state sequence, and we are using conjugate
-  priors, the VAR parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}).
+  priors, the VAR parameters converge very quickly (see Figure~\ref{fig:fixed_state_convergence}).
   Therefore, we only ran the inference procedure for 100 iterations. 
@@
   clustering approach which uses a linkage criteria in order to successively merge
-  similar clusters until a desired intracluster distance threshold or number of
+  similar clusters until a desired intra cluster distance threshold or number of
   clusters is reached.~\cite{pedregosa_scikit-learn_2011} We used the Ward linkage criteria, which works to minimize 
@@
   For our data, non-parametric methods such as Bayesian Gaussian mixture models~\cite{pedregosa_scikit-learn_2011,gelman_bayesian_2013} tend
-  to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
-  of the Supporting Information).
+  to delocalize the clusters in parameter space (see Section~\ref{section:agglomerative}
+  of Appendix D).
 
@@
   of clusters chosen.~\cite{kaufman_finding_2009} For our data, the silhouette test generally favors the 
-  lowest number of clusters possible (see Section~\ref{S-section:nclusters} of
-  the Supporting Information). However, choosing too few clusters tends to 
+  lowest number of clusters possible (see Section~\ref{section:nclusters} of
+  Appendix D). However, choosing too few clusters tends to 
   not distinguish between visually obvious differences in 
@@
 
-  \subsubsection*{The Dynamics of Methanol}
+  \subsubsection{The Dynamics of Methanol}
 
@@
   can analyze each segment sequentially and form a clear picture of this instance of 
-  methanol's behavior without the need to visualize the trajectory with software like VMD.~\cite{humphrey_vmd:_1996}
+  methanol's behavior without the need to visualize the trajectory with software like VMD.%~\cite{humphrey_vmd:_1996}
   However, it is still possible to gain a more general understanding of methanol's average
@@
   %plot of the methanol trajectory where states aren't labeled.
-  %MRS7: cross-hatching doesn't appear in the legend? Not sure which is which (I assume hatched is number density because closer to that axis).
+  %MRS7: croshatching doesn't appear in the legend? Not sure which is which (I assume hatched is number density because closer to that axis).
   %BJC7: Is it because the hatches aren't dense enough? I see them in the legend
@@
 
-  \subsubsection*{Behavior of Other Solutes}
+  \subsubsection{Behavior of Other Solutes}
 
@@
 
-  %BJC5: something we can do for the supporting information to show that this approach is valid: Eliminate nonidealities in our MD trajectories (compared to a pure VAR process) and use toy data to generate trajectories based on some number of states with different parameters.
+  %BJC5: something we can do for Appendix D to show that this approach is valid: Eliminate nonidealities in our MD trajectories (compared to a pure VAR process) and use toy data to generate trajectories based on some number of states with different parameters.
 Generate an MSD with those.
@@
   mean of the MSD. If we remove those trajectories from the MSD calculation, we obtain 
-  estimates much closer to the IHMM estimate.(I haven't done it yet, but could plot a third curve
-  with outlier removed). Acetic acid, has no obvious outliers which is consistent with our model's
-  prediction which lies within the 1$\sigma$ confidence interval of MD after a 1000 ns time lag.}\label{fig:msds}
+  estimates much closer to the IHMM estimate. Acetic acid, has no obvious outliers which is
+  consistent with our model's prediction which lies within the 1$\sigma$ confidence interval of MD 
+  after a 1000 ns time lag.}\label{fig:msds}
   \end{figure}
@@
 
-  % BJC6: I'll weaken this for the thesis, but this is what I hope to say in the 
-  % final paper.
   Finally, we show how one can generate stochastic realizations of our model that
@@
   recognize the generality of this analysis, especially in the context of molecular
-  simulations. Vector autogregressive models can describe a diverse set of behavior
+  simulations. Vector autoregressive models can describe a diverse set of behavior
   and so the IHMM may be suited to study many types motion, including those not 
@@
   which can give macroscopic insight.
-
-  \section*{Supporting Information}
-
-  Detailed explanations and expansions upon the results and procedures mentioned in
-  the main text are described in the Supporting Information. 
-  %This information is
-  %available free of charge via the Internet at http://pubs.acs.org.
-
-  \section*{Acknowledgments}
-
-  This work was supported in part by the ACS Petroleum Research Fund
-  grant \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN) 
-  fellowship which is funded by the U.S. Department of Education. 
-  Molecular simulations were performed using the Extreme Science and
-  Engineering Discovery Environment (XSEDE), which is supported by National
-  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
-  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
-  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
-  which is supported by the National Science Foundation (awards ACI-1532235 and
-  ACI-1532236), the University of Colorado Boulder, and Colorado State
-  University. The Summit supercomputer is a joint effort of the University of
-  Colorado Boulder and Colorado State University.
-
-  \clearpage
-
-  \bibliographystyle{ieeetr}
-  \bibliography{hdphmm}
-
-  %\newpage
-
-  %\section*{TOC Graphic}
-
-\end{document}
-
-% LocalWords:  BJC micropollutants Desalination permeability nanofiltration LLC
-% LocalWords:  Amphiphilic nanostructures Lyotropic amphiphilic lyotropic MSDDM
-% LocalWords:  solutes selectivities solute nanoscopic timescales MSDs MSD HMMs
-% LocalWords:  nonparameteric Parrinello Rahman barostat rescale transitioning
-% LocalWords:  al's HMM Dirichlet HDP DP Wishart TODO SI al MATLAB teh gael pdf
-% LocalWords:  nonparametric bayesian solute's reparameterized intracluster ca
-% LocalWords:  delocalize Luzar Chandler histogrammed interpolator methanol's
-% LocalWords:  nanostructure carboxylate VMD nonidealities hbonds outlier GAANN
-% LocalWords:  autogregressive PRF ACS XSEDE ACI

### 2020-04-27 Ben_Manuscripts/thesis/hdphmm_si.tex
spell checking and mod to usage of subdiffusion

--- 2020-04-13 Ben_Manuscripts/hdphmm/Supporting_Information.tex
@@
-\documentclass{article}
-
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
-\usepackage{amsmath} % or simply amstext
-\usepackage{amssymb}
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\angstrom}{\textup{\AA}}
-\newcommand{\colormap}{jet}  % colorbar to use
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\usepackage{xr}
-
-\externaldocument[M-]{Draft}
-
-\title{Supporting Information: Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
-       of Solute Trajectories in Nanostructured Membranes.}
-
-\author{Benjamin J. Coscia, Christopher P. Calderon \and Michael R. Shirts}
-
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thesection}{S\arabic{section}}
-\renewcommand{\thepage}{S\arabic{page}}
-\renewcommand{\thetable}{S\arabic{table}}
-
-\begin{document}
-
-  \graphicspath{{./supporting_figures/}}
-  \maketitle
+\chapter{Supporting Information to Chapter 5}\label{SI:ch5}
 
@@
   that follow, we graphically illustrate the procedure which is described in detail in
-  Section~\ref{M-method:IHMM} of the main text.
+  Section~\ref{method:IHMM} of Chapter 5.
 
@@
     \centering
-	\begin{subfigure}{0.8\textwidth}
+	\begin{subfigure}{0.75\textwidth}
 		\includegraphics[width=\textwidth]{xyz_hmm.pdf}
@@
 	\end{subfigure}  	
-	\begin{subfigure}{0.8\textwidth}
+	\begin{subfigure}{0.75\textwidth}
 		\includegraphics[width=\textwidth]{rz_hmm.pdf}
@@
 	\end{subfigure}  
-	\begin{subfigure}{0.8\textwidth}
+	\begin{subfigure}{0.75\textwidth}
 		\includegraphics[width=\textwidth]{zeroed_hmm.pdf}
@@
   The states identified by the IHMM are heavily influenced by the Gaussian prior
-  placed on $\mathbf{c}$ in Equation~\ref{M-eqn:var} of the main text. The 
+  placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. The 
   entries of $A$ and $\Sigma$ do not vary over a wide range, so the final
@@
 
+  When we fix the state sequence in subsequent steps of the procedure, parameter 
+  estimates converge within only a few steps. In Figure~\ref{fig:fixed_state_convergence}, we 
+  plot the entries of $A$ and $\Sigma$ as a function of IHMM iteration. Some states
+  are sampled far more frequently than others. High sampling frequently results in
+  higher certainty converged parameter estimates. Due to fast convergence, we only
+  run 100 iterations of the inference behavior when the state sequence is fixed.
+
   \begin{figure}[h]
@@
   \end{figure}
-
-  \clearpage
-
-  When we fix the state sequence in subsequent steps of the procedure, parameter 
-  estimates converge within only a few steps. In Figure~\ref{fig:fixed_state_convergence}, we 
-  plot the entries of $A$ and $\Sigma$ as a function of IHMM iteration. Some states
-  are sampled far more frequently than others. High sampling frequently results in
-  higher certainty converged parameter estimates. Due to fast convergence, we only
-  run 100 iterations of the inference behavior when the state sequence is fixed.
 
@@
 
-  \begin{figure}[h]
+  \begin{figure}[h!]
   \centering
@@
 
-  \newpage
+  \clearpage
 
@@
   \caption{We used the silhouette score test in order to quantitatively
-  inform our decision on the numbrer of clusters. Silhouette scores 
+  inform our decision on the number of clusters. Silhouette scores 
   closer to one indicate good clustering. The crosses on the plot indicate
@@
   \end{figure}
-
-\end{document}

### 2020-04-27 Ben_Manuscripts/thesis/intro.tex
Added missing intro figs
spell checking and mod to usage of subdiffusion

@@
-8\chapter{Introduction}\label{chapter:intro}
+\chapter{Introduction}\label{chapter:intro}
 
@@
   Addressing these problems with highly selective separations may lead to 
-  more signficant advances.~\cite{deshmukh_desalination_2015}
+  more significant advances.~\cite{deshmukh_desalination_2015}
 
@@
   billion people may live in water-stressed regions.~\cite{navarro-ortega_managing_2015} %There's a water stress index in fritzmann_2007
-  Membrane deslination via RO and thermal muli-stage flash distillation are 
+  Membrane desalination via RO and thermal multi-stage flash distillation are 
   both widely used processes for creating potable water in these regions.~\cite{fritzmann_state---art_2007}
@@
   into our drinking water supply.~\cite{barbosa_occurrence_2016} Sources of micropollutants
-  incude industrial wastewater, agricultural runoff, landfill leachates and domestic 
+  include industrial wastewater, agricultural runoff, landfill leachate and domestic 
   effluents.~\cite{mompelat_occurrence_2009} Unfortunately, most waste water treatment 
@@
   \caption{(a) Pristine graphene (left) and graphene oxide (right) are atomically thick,
-  offering the potential for high permeabilities. (b) Carbon nanotubes exhibit extemely
+  offering the potential for high permeabilities. (b) Carbon nanotubes exhibit extremely
   fast water transport due to their hydrophobic interiors. (c) Zeolites, like ZK-4 
@@
   One can replace the silicon and aluminum atoms via ion exchange in order
-  to control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}
+  to control the size of the cavities and hence its molecular-sieving properties.~\cite{li_novel_2007}
 
   A number of studies have tested the permeability and sodium salt rejection
-  of various zeolite membranes, however their high permeabilities typcially come
+  of various zeolite membranes, however their high permeabilities typically come
   at the cost of low selectivities and vice versa.~\cite{li_desalination_2004,duke_seawater_2009}
@@
   uniform-sized pores on the order of 1 nm in size.~\cite{gin_polymerized_2008}
-  As shown in Figure TBD, monomer 1 will form the inverted hexagonal phase 
+  As shown in Figure~\ref{fig:lc_phases}, monomer 1 will form the inverted hexagonal phase 
   (H\textsubscript{II})~\cite{smith_ordered_1997} while monomer 2 will form the 
@@
   Although the Q\textsubscript{I} phase has a much more tortuous network of 
-  pores than the H\textsubscript{II}, which should lower its relative permeabily,
+  pores than the H\textsubscript{II}, which should lower its relative permeability,
   its synthesis is much more practical because it does not require alignment of
@@
     	  whose dominance is dependent on solute chemical functionality. We characterize
-    	  three different trapping mechanisms which lead to subdiffusive transport behavior.
+    	  three different trapping mechanisms which lead to subdiffusive transport behavior
+    	  %BJCF: added
+    	  on the timescales of our simulations.
 
@@
     	  behavior on MD simulation-length timescales. We then show how we can use our 
-    	  most promsiing model in order to connect microscopic transport to macroscopic
+    	  most promising model in order to connect microscopic transport to macroscopic
     	  flux and selectivity.

### 2020-04-27 Ben_Manuscripts/thesis/stochastic_transport.tex
spell checking and mod to usage of subdiffusion

--- 2020-02-07 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
@@
-\documentclass[aps,pre,preprint,groupedaddress,longbibliography]{revtex4-2}
-\usepackage{CJK}
-
-\usepackage{multirow}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-%\usepackage{caption}
-\usepackage{amsmath} % or simply amstext
-\usepackage{amssymb}
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\usepackage{xr}
-\usepackage{diagbox}
-\usepackage{array}
-
-\DeclareUnicodeCharacter{03C9}{$\omega$}
-%\usepackage[en]{babel}
-
-\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
-\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
-\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
-\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
-\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
-\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
-
-\externaldocument[S-]{Supporting_Information}
-
-\begin{document}
-
-  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
+\chapter{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
   with Time Series Modeling}
 
-  \author{Benjamin J. Coscia}
-  \author{Michael R. Shirts}
-
-  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}
-
-  \date{\today}
-
-  \begin{abstract}
-
-  Mathematically modeling complex transport phenomena at the molecular level 
-  can be a powerful tool for identifying transport mechanisms and predicting
-  macroscopic properties. We use two different stochastic time series models,
-  parameterized from long molecular dynamics (MD) simulation trajectories of
-  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
-  membrane, in order to predict solute mean squared displacements (MSDs) 
-  and solute flux, and thus solute selectivity, in macroscopic length pores.
-
-  First, using anomalous diffusion theory, we show how solute dynamics can be
-  modeled as a fractional diffusion process subordinate to a continuous time 
-  random walk. From the MD simulations, we parameterize the distribution of 
-  dwell times, hop lengths between dwells and correlation between hops. We 
-  explore two variations of the anomalous diffusion modeling approach. The first variation
-  applies a single set of parameters to the solute displacements and the second
-  applies two sets of parameters based on the solute's radial distance from the
-  closest pore center.
-
-  Next, we generalize Markov state models, treating the
-  configurational states of the system as a Markov process where each
-  state has distinct transport properties. For each state and transition
-  between states, we parameterize the distribution and temporal correlation 
-  structure of positional fluctuations as a means of characterization and to 
-  allow us to predict solute MSDs. We show that both models reasonably reproduce
-  the MSDs calculated from MD simulations. However, qualitative differences 
-  between MD and Markov state dependent model-generated trajectories may limit 
-  its usefulness.
-
-  Finally, we demonstrate how one can use these models to 
-  estimate flux of a solute across a macroscopic-length pore and, based on 
-  those quantities, the membrane's selectivity towards each solute. This work 
-  helps to connect microscopic chemically-dependent solute motions that do not
-  follow simple diffusive behavior with macroscopic membrane performance.
-
-  \end{abstract}
-
-  \maketitle
-
-  \graphicspath{{./figures/}}
-
   \section{Introduction}
-
-  Highly selective separations membranes are desirable in numerous
-  applications. The ability to efficiently separate ions from saline water
-  sources using membranes has been actively pursued for years in an effort to
-  create potable water for people in water-scarce
-  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
-  supplies, there is a need for membranes that can specifically separate
-  potentially harmful organic micropollutants such as fertilizers, pesticides,
-  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} In
-  the materials industry, there is a strong interest in creating breathable
-  fabrics which selectively allow passage of water
-  vapor.~\cite{mondloch_destruction_2015}
-
-  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
-  can be cross-linked into mechanically strong and highly selective nanoporous
-  membranes.~\cite{gin_polymerized_2008} They may provide a promising
-  alternative to conventional membrane separation techniques by being selective
-  based not only on solute size and charge, but on solute chemical
-  functionality as well.~\cite{dischinger_application_2017} One can tune the
-  functionality of LLC monomers in order to enhance or weaken specific
-  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
-  morphologies of LLC membranes are being actively developed. The inverted
-  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
-  pores on the order of 1 nm in size. A perfectly synthesized
-  H\textsubscript{II} phase has an ideal geometry for high throughput
-  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
-  a large scale as required for high permeability has shown limited
-  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
-  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
-  complex pores of the H\textsubscript{II} phase but its geometry consists of a
-  tortuous network of 3D interconnected pores which do not require
-  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
-  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
-  H\textsubscript{II} phase, it is considerably easier to produce 
-  at scale.~\cite{hatakeyama_nanoporous_2010}
-
-  Molecular modeling may make it possible to efficiently evaluate
-  solute-specific separation membranes using the available chemical space of
-  LLC monomers. To date, only a limited subset of LLC monomers have been
-  studied experimentally in membrane applications.
-  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
-  Even within this small subset, they have demonstrated selectivities that
-  could not be explained beyond speculation and vague empirical
-  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
-  can provide the resolution necessary to identify molecular interactions that
-  are key to separation mechanisms, allowing us to move beyond Edisonian design
-  approaches.
 
@@
   Q\textsubscript{I} phase and significantly more structural data is available
-  to help ensure molecular models are consistent with experiment. In general,
+  to help ensure molecular models are consistent with experiment. 
+  %BJCF: modified  
+  %In general,
+  On MD simulation timescales, 
   we observed subdiffusive transport behavior characterized by intermittent
@@
   descriptions of a much more diverse set of behavior, including subdiffusion,
-  a type of anomalous diffusion exhibited by solutes in this
-  study.~\cite{klages_anomalous_2008}
+  a type of anomalous diffusion exhibited by solutes
+  %in this study.~\cite{klages_anomalous_2008}
+  %BJCF: modified
+  on the simulation timescales of this study.~\cite{klages_anomalous_2008}
 
@@
   scripts to use for subsequent calculations are summarized in
-  Table~\ref{S-table:python_scripts} of the Supplemental Material.
+  Table~\ref{table:python_scripts} of Appendix C.
 
@@
   in our analysis of solute kinetics. We plot the solute partition versus time in
-  Figure~\ref{S-fig:equilibration} of the Supplemental Material in order to justify
+  Figure~\ref{fig:equilibration} of Appendix C in order to justify
   our choice of equilibration times for each solute.
@@
 
-  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
+  %BJCF: added
+  On the timescales simulated in this study,
+  solutes in this system very clearly exhibit subdiffusive behavior, a type of
   anomalous diffusion. During an anomalous diffusion process, the mean squared 
@@
   we do not simulate enough independent solute trajectories to obtain a reliable
-  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
+  estimate. 
+  %BJCF: added next two sentences
+  It is also possible that solute dynamics will become diffusive on
+  long simulation timescales. Therefore, the transition from subdiffusion to regular
+  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD curves. 
+  We can obtain higher precision estimates of $\alpha$ using the dwell
   time distributions described in subsequent sections.
@@
   \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
-  \label{eqn:ensemble_msd}
+  \label{eqn:ensemble_msd2}
   \end{equation}
@@
   \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
-  \label{eqn:tamsd}
+  \label{eqn:tamsd2}
   \end{equation}
@@
   Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
-  Figure~\ref{S-fig:hurst_autocorrelation} of the Supplemental Material). Any hope of
+  Figure~\ref{fig:hurst_autocorrelation} of Appendix C). Any hope of
   fitting longer time lags to our data is lost in the noise since the analytical values
@@
   from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
-  See Section~\ref{S-section:H_estimate} of the Supplemental Material for numerical
+  See Section~\ref{section:H_estimate} of Appendix C for numerical
   simulations illustrating this point.
@@
   to deviate from the empirically measured PDF (see
-  Section~\ref{S-section:truncation} of the Supplemental
-  Material).~\cite{mantegna_stochastic_1994}
-
-  \subsubsection*{Multiple Anomalous Diffusion Regimes}
+  Section~\ref{section:truncation} of Appendix C).~\cite{mantegna_stochastic_1994}
+
+  \subsubsection{Multiple Anomalous Diffusion Regimes}
 
@@
 
-  \subsubsection*{Simulating Anomalous Diffusion}
+  \subsubsection{Simulating Anomalous Diffusion}
 
@@
 
-  We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
+  We used Equation~\ref{eqn:tamsd2} to calculate the time-averaged MSD of the MD
   and AD model trajectories then estimated their uncertainty using statistical
@@
   We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
-  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
-  the Supplemental Material) of the algorithm by Stoev and Taqqu to
+  and our own Python implementation (see Table~\ref{table:python_scripts} of
+  Appendix C) of the algorithm by Stoev and Taqqu to
   simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
@@
   correction to enhance the accuracy of the correlation structure (see
-  Section~\ref{S-section:flm_correlation} of the Supplemental Material for
+  Section~\ref{section:flm_correlation} of Appendix C for
   validation of the approach).
@@
   verified the Markovianity of state transitions as described in
-  Section~\ref{S-section:markov_validation} of the Supplemental Material.
+  Section~\ref{section:markov_validation} of Appendix C.
 
@@
   Equation~\ref{eqn:passage_times} is given in
-  Section~\ref{S-section:fpt_derivation} of the Supplemental Material. We
+  Section~\ref{section:fpt_derivation} of Appendix C. We
   calculated the expected value of Equation~\ref{eqn:passage_times} in order to
@@
 	  show similar distributions and autocorrelation functions (see
-	  Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
+	  Figure~\ref{fig:anticorrelated_hops} of Appendix C).
   }\label{fig:anticorrelated_hops}
@@
   Predictions made with these models consistently under-predict the MD MSDs
-  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supplemental
-  Material). Therefore, we will not include the pure sFBM or sFLM models in the
-  remainder of our analysis.
+  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of Appendix C). Therefore, we 
+  will not include the pure sFBM or sFLM models in the remainder of our analysis.
 
@@
   shapes of urea and acetic acid's MSD curves are also very similar (see
-  Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).
+  Figure~\ref{fig:msd_comparison} of Appendix C).
 
@@
   measured from MD simulations within or near statistical uncertainty. In
-  Figure~\ref{S-fig:train_test} of the Supplemental Material, we parameterized
+  Figure~\ref{fig:train_test} of Appendix C, we parameterized
   the AD models using the first half of the stationary solute equilibrated
@@
   equilibration time. The MSD curves generated from both the one and 
-  two mode models are overlayed with the MD simulated MSDs for comparison in
+  two mode models are overlaid with the MD simulated MSDs for comparison in
   Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
@@
   However, the modeled trajectories undershoot the mean MD MSD as the time lag
-  increases. As discussed in the previous section, long time positional
-  anti-correlation, on the order of hundreds of ns, may not exist in the MD
-  system. Eventual loss of correlation would result in a shift from sub-linear
-  to linear MSD behavior, as observed in the MD trajectories. Acetic acid
-  exemplifies this point. At first glance, acetic acid's predicted MSD appears
+  increases. 
+  %BJCF: I don't think this is discussed in the previous section.
+  % As discussed in the previous section, 
+  %BJCF: Rest of this paragraph already addresses Matt's point. I added "...,or subdiffusive,...,or diffusive," to make explicit
+  Long time positional anti-correlation, on the order of hundreds of ns, may not
+  exist in the MD system. Eventual loss of correlation would result in a shift from
+  sub-linear, or subdiffusive, to linear, or diffusive, MSD behavior, as observed in the MD trajectories.   
+  Acetic acid exemplifies this point. At first glance, acetic acid's predicted MSD appears
   to match the curvature of MD quite well, but closer examination reveals that
@@
   and methanol are relatively similar, which is consistent with their similar MD
-  MSDs and qualitatively similar MD timeseries.
+  MSDs and qualitatively similar MD time series.
   Relative to ethylene glycol, methanol tends to stay trapped for less
@@
   parameters are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated
-  in the Supplemental Material, Table~\ref{S-table:msddm_params}).
+  in Appendix C, Table~\ref{table:msddm_params}).
 
@@
   longer. One could improve performance significantly by simulating less
-  trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supplemental
-  Material, we determined that one can simulate as few as 100 sFBMcut
+  trajectories. In Figure~\ref{fig:flux_curve_sensitivity} of Appendix C,
+  we determined that one can simulate as few as 100 sFBMcut
   realizations in order to parameterize Equation~\ref{eqn:flux_decay}. For
@@
 	  similar fits for the remaining solutes in
-	  Figure~\ref{S-fig:ad_fpt_fits} of the Supplemental Material. (b) The
+	  Figure~\ref{fig:ad_fpt_fits} of Appendix C. (b) The
 	  single particle flux measured by the sFBMcut AD model decays with
@@
   value of $\beta$ when $H$=0.5. We further verified this claim by removing
-  hop anti-correlation and setting all dwell times equal to one timestep,
+  hop anti-correlation and setting all dwell times equal to one time step,
   effectively simulating Brownian motion.  The length dependence remains
@@
   AD models continuously curve. This is because pure fractional Brownian motion
-  features hop correlation that persists indefinitely. We may be able to
-  address this by truncating the positional autocorrelation function, allowing
+  features hop correlation that persists indefinitely. 
+  %BJCF: added following sentence
+  However, it is likely that on longer timescales, hops become decorrelated, 
+  causing solute dynamics to transition from subdiffusive to diffusive behavior.
+  We may be able to
+  incorporate this transition %<-- BJCF: added%
+  % address this 
+  by truncating the positional autocorrelation function, allowing
   correlation to diminish on the 100 ns timescale as suggested by the physical
@@
   facilitate new ways of approaching complex separation problems.
-
-  \section*{Supplemental Material}
-
-  Detailed explanations and expansions upon the results and procedures
-  mentioned in the main text are described in the Supplemental Material. This
-  information is available free of charge via the Internet at
-  http://pubs.acs.org.
-
-  \section*{Acknowledgments}
-
-  We thank Richard Noble for helping us make the connection between the empirical 
-  mean first passage time distribution and the analytical equation to which we fit
-  the distributions (Equation~\ref{eqn:passage_times}).
-
-  This work was supported in part by the ACS Petroleum Research Fund grant
-  \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN)
-  fellowship which is funded by the U.S. Department of Education.  Molecular
-  simulations were performed using the Extreme Science and Engineering
-  Discovery Environment (XSEDE), which is supported by National Science
-  Foundation grant number ACI-1548562. Specifically, it used the Bridges
-  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
-  Supercomputing Center (PSC). This work also utilized the RMACC Summit
-  supercomputer, which is supported by the National Science Foundation (awards
-  ACI-1532235 and ACI-1532236), the University of Colorado Boulder, and
-  Colorado State University. The Summit supercomputer is a joint effort of the
-  University of Colorado Boulder and Colorado State University.
-
-  %\bibliographystyle{apsrev4-2}
-  \bibliography{stochastic_transport}
-
-  % No TOC image in PRE
-  %\section*{TOC Graphic}
-
-  %\begin{figure}[!htb]
-  %\centering
-  %\includegraphics[width=3.25in]{toc.pdf}
-  %\end{figure}
-
-\end{document}
-
-% LocalWords:  solute MSDs solutes solute's LLC BJC nanoporous maginn Lyotropic
-% LocalWords:  micropollutants LLCs amphiphilic mesophases feng Bicontinuous EG
-% LocalWords:  permeability hatakeyama zhou resel selectivities Edisonian CTRW
-% LocalWords:  subdiffusive timescale timescales subdiffusion FBM RWF metzler
-% LocalWords:  jeon neusius pdf Sokolov ony MSD MSMs chodera MSM AcOH URE MeOH
-% LocalWords:  Hbonding hbonds hbond GROMACS berendsen gromacs der spoel hess
-% LocalWords:  wt Na GA carboxylate Parrinello Rahman barostat rescale msd dt
-% LocalWords:  superdiffusive EB sFBM min Hurwitz factoid MLEs autocovariance
-% LocalWords:  evy sFLM FLM sFLMcut Dirichlet saiid fbm Stoev Taqqu MLE TODO SI
-% LocalWords:  vvvv wehmeyer MSMbuilder pyEMMA featurization Phys Chem bayesian
-% LocalWords:  Markovianity MSDDMs MSDDM resampling TBD MSD's CTRWs GCL acf ACH
-% LocalWords:  urea's alkane overlayed SFLMcut underpredicted Gaussians HMM PRF
-% LocalWords:  params msddm timeseries overpredicted GAANN ACS XSEDE ACI PSC QI
-% LocalWords:  RMACC TOC Nanoscale Coscia lyotropic morphologies HII geens MFPT
-% LocalWords:  darvishmanesh bouchaud integrator LINCS clauset sFBMcut pyemma
-% LocalWords:  msmbuilder diffusivity Eq vt dz erfc permeabilities Kedem zoubi
-% LocalWords:  Katchalsky's nanofiltration ultrafiltration trans convective py
-% LocalWords:  bothmode todo eyetest Methanol's acid's subplots methanol's alt
-% LocalWords:  timestep pre selectivtiy foulants subfigures RWFs roman github
-% LocalWords:  al linkable nanopores

### 2020-04-27 Ben_Manuscripts/thesis/stochastic_transport_si.tex
spell checking and mod to usage of subdiffusion

--- 2020-01-28 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
@@
-\documentclass{article}
-
-% Table of contents formatting
-\usepackage{tocloft}
-
-\renewcommand\cftsecfont{\normalfont}
-\renewcommand\cftsecpagefont{\normalfont}
-\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}}
-\renewcommand\cftsecdotsep{\cftdot}
-\renewcommand\cftsubsecdotsep{\cftdot}
-\cftsetindents{section}{0em}{3em}
-%\cftsetindents{subsection}{1em}{3em}
-
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
-\usepackage{amsmath}
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage[export]{adjustbox}
-\newcommand{\colormap}{jet}  % colorbar to use
-\usepackage{cleveref}
-\usepackage{booktabs}
-\usepackage{gensymb}
-\usepackage{float}
-\usepackage{xr}
-\usepackage{array}
-\usepackage{multirow}
-
-\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
-\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
-\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
-\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
-\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
-\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
-
-\externaldocument[M-]{Final_Draft}
-
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thesection}{S\arabic{section}}
-\renewcommand{\thepage}{S\arabic{page}}
-\renewcommand{\thetable}{S\arabic{table}}
-
-\title{Supplemental Material: Capturing Subdiffusive Solute Dynamics and 
-Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
-\author{Benjamin J. Coscia \and Michael R. Shirts}
-
-\begin{document}
-
-  \maketitle
-  %MRS10: be consistent on capitalization of section titles (And therefore table of contents)
-  \tableofcontents
-  \graphicspath{{./supporting_figures/}}
-  \bibliographystyle{ieeetr}
-
-  \newpage
+\chapter{Supporting Information to Chapter 4}\label{SI:ch4}
 
@@
 
-  \section{Solute Equilibration}\label{section:equilibration}
+  \section{Solute Equilibration}\label{S-section:equilibration4}
 
@@
   autocorrelation function for fractional Brownian motion (the variance-normalized version 
-  of Equation~\ref{M-eqn:fbm_autocorrelation} in the main text):
+  of Equation~\ref{eqn:fbm_autocorrelation} in Chapter 4):
 
@@
     \gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
-  \label{eqn:fbm_autocorrelation}
+  \label{S-eqn:fbm_autocorrelation}
   \end{equation}
 
-  In Figure~\ref{fig:hurst_autocorrelation}, we plotted Equation~\ref{eqn:fbm_autocorrelation}
-  for different values of $H$. When $H > 0.5$, Equation~\ref{eqn:fbm_autocorrelation} decays
+  In Figure~\ref{fig:hurst_autocorrelation}, we plotted Equation~\ref{S-eqn:fbm_autocorrelation}
+  for different values of $H$. When $H > 0.5$, Equation~\ref{S-eqn:fbm_autocorrelation} decays
   slowly to zero meaning one needs to study large time lags with high frequency in order to
   accurately estimate $H$ from the data. Fortunately, all of our solutes show anti-correlated
-  motion, so most of the information in Equation \ref{eqn:fbm_autocorrelation} is contained
+  motion, so most of the information in Equation \ref{S-eqn:fbm_autocorrelation} is contained
   within the first few lags.
@@
   The autocovariance function of fractional L\'evy motion is different from fractional
-  Brownian motion (see Equations~\ref{M-eqn:fbm_autocorrelation}
-  and~\ref{M-eqn:flm_autocovariance} of the main text), but their autocorrelation 
+  Brownian motion (see Equations~\ref{eqn:fbm_autocorrelation}
+  and~\ref{eqn:flm_autocovariance} of the main text), but their autocorrelation 
   structures are the same. The autocovariance function of FLM is dependent on the 
@@
   a well-defined structure and is independent of the coefficient in 
-  Equation~\ref{M-eqn:flm_autocovariance} of the main text. In Figure~\ref{fig:flm_autocorrelation}, 
+  Equation~\ref{eqn:flm_autocovariance} of the main text. In Figure~\ref{fig:flm_autocorrelation}, 
   we plot the average autocorrelation function from an FLM process with an increasing 
@@
   \end{subfigure}
-  \caption{As the timestep between observations increases, the probability
+  \caption{As the time step between observations increases, the probability
   transition matrix does not change significantly.}\label{fig:transitions}
@@
   To derive an analytical equation for the mean first passage time 
-  (Equation~\ref{M-eqn:passage_times} of the main text), first consider an 
+  (Equation~\ref{eqn:passage_times} of Chapter 4), first consider an 
   initial pulse spreading out over time with a fixed mean. We can solve for the 
@@
   P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
-  \label{eqn:passage_times}
+  \label{S-eqn:passage_times}
   \end{equation} 
   where the only free parameters for fitting are $v$ and $D$. We calculated the
-  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT. Specifically,
+  expected value of Equation~\ref{S-eqn:passage_times} in order to get the MFPT. Specifically,
   we used the python package \texttt{scipy.integrate.quad} to numerically integrate:
@@
 
-  Analogous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
-  Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the
+  Analogous to Figure~\ref{fig:anticorrelated_hops},
+  Figure~\ref{S-fig:anticorrelated_hops} demonstrates that all solutes exhibit the
   same kind of anti-correlated hopping and trapping behavior.
@@
   respectively for ethylene glycol (a-c), acetic acid (d-f) and methanol (g-i).
-  See Section~\ref{M-section:AD_parameterization} of the main text for a more detailed discussion.
-  }\label{fig:anticorrelated_hops}
+  See Section~\ref{section:AD_parameterization} of the main text for a more detailed discussion.
+  }\label{S-fig:anticorrelated_hops}
   \end{figure}
@@
   the simulation length into simulated trajectories 
-  (see Figure~\ref{fig:anomalous_msds_bothmode}). The parameters of the pure power law 
+  (see Figure~\ref{S-fig:anomalous_msds_bothmode}). The parameters of the pure power law 
    distribution are included in Figure~\ref{fig:pure_power_law_params}.
@@
   \includegraphics[width=\textwidth]{bothmode_msd_comparison_URE.pdf}
-  \caption{Urea}\label{fig:bothmode_msd_comparison_URE}
+  \caption{Urea}\label{S-fig:bothmode_msd_comparison_URE}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{bothmode_msd_comparison_GCL.pdf}
-  \caption{Ethylene Glycol}\label{bothmode_msd_comparison_GCL}
+  \caption{Ethylene Glycol}\label{S-bothmode_msd_comparison_GCL}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{bothmode_msd_comparison_MET.pdf}
-  \caption{Methanol}\label{fig:bothmode_msd_comparison_MET}
+  \caption{Methanol}\label{S-fig:bothmode_msd_comparison_MET}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{bothmode_msd_comparison_ACH.pdf}
-  \caption{Acetic Acid}\label{fig:bothmode_msd_comparison_ACH}
+  \caption{Acetic Acid}\label{S-fig:bothmode_msd_comparison_ACH}
   \end{subfigure}
@@
   AD model.
-  }\label{fig:anomalous_msds_bothmode}
+  }\label{S-fig:anomalous_msds_bothmode}
   \end{figure}
@@
   \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
-  \caption{}\label{fig:1mode_AD_dwells}
+  \caption{}\label{S-fig:1mode_AD_dwells}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
-  \caption{}\label{fig:2mode_AD_dwells}
+  \caption{}\label{S-fig:2mode_AD_dwells}
   \end{subfigure}
@@
   Pure power laws have an infinite variance which allows extremely long dwell
-  times to be sampled (see Figure~\ref{fig:anomalous_msds_bothmode}.
+  times to be sampled (see Figure~\ref{S-fig:anomalous_msds_bothmode}).
   }\label{fig:pure_power_law_params}
@@
   only meaningful if the ensemble of solute trajectories is stationary. In 
-  Figure~\ref{fig:msd_comparison}, we show that urea and acetic acid show acceptable
+  Figure~\ref{S-fig:msd_comparison}, we show that urea and acetic acid show acceptable
   stationary behavior while methanol and ethylene glycol do not.
@@
   similar MSDs, providing evidence of stationarity, while the MSDs of 
-  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
+  ethylene glycol and methanol are different suggesting that they are not.}\label{S-fig:msd_comparison}
   \end{figure}
@@
 %  because the Hurst parameter is challenging to quantify, especially with a relatively 
-%  small amount of data (see Section~\ref{M-method:sfbm} of the main text for further discussion of this 
+%  small amount of data (see Section~\ref{method:sfbm} of the main text for further discussion of this 
 %  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
@@
   The tables in this section are tabular representations of the parameters depicted in
-  Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the main text
-  and used to generate AD approach realizations whose MSDs are shown in Figure~\ref{M-fig:anomalous_msds}
+  Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters} of the main text
+  and used to generate AD approach realizations whose MSDs are shown in Figure~\ref{fig:anomalous_msds}
   of the main text.
@@
   The following table is a tabular representation of the parameters 
-  depicted in Figure~\ref{M-fig:msddm_parameters} of the main text.
+  depicted in Figure~\ref{fig:msddm_parameters} of the main text.
 
@@
   trajectories and used them to generate realizations of our MSDDM model. The states
-  are defined in Table~\ref{M-table:states} of the main text except state T which 
+  are defined in Table~\ref{table:states} of the main text except state T which 
   describes the transition emissions.}\label{table:msddm_params}
@@
 %  \caption{Values of $H$, $\alpha_h$ and $\sigma$ used to simulate realizations
-%  of the simple MSDDM whose MSDs are shown in Figure~\ref{M-fig:T_sensitivity} of
-%  the main text. The values are chosen to be similar to those in Table~\ref{M-table:msddm_params}
+%  of the simple MSDDM whose MSDs are shown in Figure~\ref{fig:T_sensitivity} of
+%  the main text. The values are chosen to be similar to those in Table~\ref{table:msddm_params}
 %  of the main text.}\label{table:msddm_params}
@@
   \end{subfigure}
-  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
+  \caption{We fit Equation~\ref{eqn:passage_times} of Chapter 4 to the
   first passage time distributions generated by 10,000 realizations of the 
@@
 %  \end{subfigure}
-%  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
+%  \caption{We fit Equation~\ref{eqn:passage_times} of the main text to the
 %  first passage time distributions generated by 1000 realizations of the 
@@
   as few as 100 independent realizations of the sFBMcut AD model. To estimate
-  $A$, we fit Equation~\ref{M-eqn:flux_decay} of the main text to a series of
+  $A$, we fit Equation~\ref{eqn:flux_decay} of the main text to a series of
   flux measurements made with 10, 15, 20, 25, 30, 35, 40, 45 and 50 nm pores (see
-  Figure~\ref{M-fig:flux_curves_ad} of the main text).
+  Figure~\ref{fig:flux_curves_ad} of the main text).
   }\label{fig:A_sensitivity}
@@
   \end{figure}
-
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
-%  \caption{100 Independent Trajectories}\label{fig:N100}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
-%  \caption{1000 Independent Trajectories}\label{fig:N1000}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
-%  \caption{5000 Independent Trajectories}\label{fig:N5000}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
-%  \caption{10000 Independent Trajectories}\label{fig:N10000}
-%  \end{subfigure}
-%  \caption{Even using a small number of independent trajectories, one can
-%  reliably calculate flux as a function of pore length. The uncertainty in
-%  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
-%  \end{figure}
-  %MRS8: is there a way to make it easier to see the fact that the data is relatively independent of length?
-  %MRS8: Right now, you essentially have to scan between the 4 charts to see the numbers are about right. Maybe
-  %MRS8: organize it so that the 4 charts are for 4 molecules, and each chart shows plot of 
-  %MRS8: trajectory number vs pore length, so one can see that the value stays about the same except for uncertainty as 
-  %MRS8: number of trajectories changes
-  % equations here 
-  % Analytical CDF: https://journals.aps.org/pre/pdf/10.1103/PhysRevE.73.046104
-  % Analytical MFPT https://journals.aps.org/pre/pdf/10.1103/PhysRevE.62.6065
-  % Figures: mfpt_pdf.pdf and mfpt_cdf.pdf
-
-%  \newpage
-%
-%  \section{Explanation of Under-Estimated MSDDM $\beta$ Values}\label{section:beta_estimates}
-%  
-%  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
-%  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
-%  Turning first to the model itself, we have designed it to ensure that the magnitude of the
-%  hops in the series of transitions between states are anti-correlated from start to finish. 
-%  This assumes that the transition correlation structure is unaffected by the
-%  sub-trajectories between each state transition. Each time a state transition occurs, one
-%  must initialize a new time series sub-trajectory with its own correlation structure. 
-%  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
-%  %in each state is relatively short making the accuracy of the correlation structure 
-%  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
-%  %$\sigma$ in trapped states. 
-%  Since we add the transitional hop lengths to each end of
-%  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
-%  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
-%  MSDDM to completely immobilize particles except when they transition between states. 
-%  Surprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
-%  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
-%  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
-%  To generate the curves in Figure~\ref{M-fig:flux_curves_msddm}, we needed to correlate 
-%  25--1000 times more hops than for the MSD predictions in Figure~\ref{M-fig:msddm_performance}. 
-%  In short, it is computationally infeasible to use enough terms to accurately incorporate
-%  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
-%  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
-%  fractional Brownian motion, for which we have an exact simulation method, in place of 
-%  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
-%  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
-%  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
-%  of FLM.  
-%  
-%  \begin{figure}[h]
-%  \centering
-%  \begin{subfigure}{0.43\textwidth}
-%  \includegraphics[width=\textwidth]{beta_hurst.pdf}
-%  \caption{}\label{fig:beta_hurst}
-%  \end{subfigure}
-%  \begin{subfigure}{0.52\textwidth}
-%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
-%  \caption{}\label{fig:beta_parameters}
-%  \end{subfigure}
-%  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
-%  %MRS6: should try to lead with what the overall results/conclusions are.
-What does it mean that parameters are larger or smaller?
-What should the reader take from the discussion?
-Should it be in supporting?
-%  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
-%  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
-%  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
-%  sub-trajectories between state transitions decorrelate transitional hops and because
-%  our FLM simulation procedure does not accurately correlate hops after long time lags. 
-%  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
-%  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
-%  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
-%  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
-%  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
-%  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
-%  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
-%  \end{figure}
-
-  \clearpage
-  \bibliography{stochastic_transport}
-
-\end{document}
-
-% LocalWords:  LLC solutes py equispaced solute's ctrw sfbm ctrwsim MSD solute
-% LocalWords:  MSDDM XXXX GitHub plateaued Meroz Sokolov superdiffusion MSDs wt
-% LocalWords:  subdiffusion msd PR nojump xtc gro ETH nboot pdf subdiffusive xr
-% LocalWords:  RWF brownian FBM CTRWs traj npt fracshow Taqqu recentering MFPT
-% LocalWords:  Markovianity timestep GCL acf ACH bothmode params BJC tex acid's
-% LocalWords:  sFBMcut sFLMcut urea's timescale msddm fpt CDF mfpt cdf hurst
-% LocalWords:  decorrelate nanopore FLM autocovariance evy undersampling Stoev
-% LocalWords:  undersampled URE timescales Nsensitivity Asensitivity
-% LocalWords:  betasensitivity

### 2020-04-27 Ben_Manuscripts/thesis/structure.tex
spell checking and mod to usage of subdiffusion

@@
   \section{Introduction}
-
-%  More highly selective nanoporous membranes would be extremely useful for
-%  performing complex aqueous separations with seawater and various types of
-%  wastewater. For example, Sodium chloride and boron in seawater
-%  \cite{fritzmann_state---art_2007} and organic micropollutants found in
-%  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
-%  represent just a few of the diverse contaminants of water sources. By
-%  efficiently separating contaminants from feed solutions with highly selective
-%  membranes, it is possible to reduce the number of required membrane passes and
-%  post-treatment steps needed for a given filtration process
-%  \cite{werber_materials_2016}, thus lowering energy requirements. Additionally,
-%  one can also extract valuable resources from the feed streams. For example,
-%  flowback water produced during hydraulic fracturing of shale formations
-%  contains dissolved species such as acetate whose extraction has economic value
-%  \cite{dischinger_application_2017}.  
-%
-%  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
-%  filtration processes that can be used to separate solutes on the order of 1 nm
-%  in size and smaller, including ions. However, commercially available amorphous
-%  RO membranes and porous NF membranes lack uniformity, which severely impacts
-%  their selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
-%  fabrication involves the spontaneous assembly of polymers into disordered
-%  structures that offer separation pathways that are tortuous and polydisperse in
-%  size \cite{werber_materials_2016}. Tortuosity increases the effective length
-%  that a solute must travel, while pore size polydispersity limits membrane
-%  selectivity.
-%
-%  Ordered, nanostructured porous membrane materials have become an increasingly popular
-%  research area for aqueous separation applications because they offer the
-%  ability to control pore architecture at the molecular scale, thereby
-%  permitting the design of solute-specific separation membranes
-%  \cite{humplik_nanostructured_2011}. However, their development has been limited
-%  by the ability to synthesize and scale various technologies. Graphene sheets
-%  are atomically thick, which results in excellent water permeability but defects
-%  during manufacturing severely impact selectivity
-%  \cite{cohen-tanugi_multilayer_2016}.  Molecular dynamics (MD) simulations of
-%  carbon nanotubes have shown promise \cite{humplik_nanostructured_2011}, but
-%  synthetic techniques are unable to achieve scalable alignment and pore
-%  monodispersity \cite{hata_water-assisted_2004,maruyama_growth_2005}.
-%  Consequently, there is a need for new materials that could provide scalable
-%  nanostructured porous membranes. 
-%
-%  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
-%  (LLC) membranes can be produced at moderate scale and may be capable of
-%  performing highly selective separations. LLCs are amphiphilic molecules that
-%  have the ability to self-assemble into porous nanostructures
-%  \cite{smith_ordered_1997} and can be cross-linked to create mechanically strong
-%  membrane films with periodic pores on the order of 1 nm in diameter
-%  \cite{zhou_supported_2005}. Unlike the pores in most commercial NF membranes,
-%  polymeric LLC membrane pores are uniform in size because they are formed by
-%  self-assembly. Since LLC polymer membranes lack an appreciable pore size
-%  distribution, they inherently exhibit high selectivity due to their strict
-%  molecular weight cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the
-%  LLC monomers examined in this paper are salts, and therefore lead to Donnan
-%  exclusion of ions in solution. The membrane gains a net surface charge when
-%  counterions from the head groups that line the pore walls escape into the feed
-%  solution in an effort to balance the gradients of concentration and electric
-%  potential \cite{donnan_theory_1995}.    
-%
-%  The feasibility of nanostructured LLC polymer membranes for selective
-%  separations has been demonstrated using LLC monomers that form the type 1
-%  bicontinuous cubic (Q\textsubscript{I})
-%  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
-%  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
-%  phases. When separating organic solutes from NaCl, Q\textsubscript{I}-phase
-%  membrane filtration experiments have shown selectivity 2--3 times higher than
-%  commercial RO and 6--12 times higher than commercial NF membranes
-%  \cite{dischinger_application_2017}. When separating a series of various sized
-%  dyes, the H\textsubscript{II}-phase membrane showed complete rejection of dyes
-%  bigger than 1.2 nm in size \cite{zhou_supported_2005}. 
-%
-%  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:hex_packing_simple}) has a
-%  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
-%  The H\textsubscript{II} phase forms at room temperature in the presence of
-%  ca.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
-%  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
-%  form the same hexagonal columnar structure which, in the literature, has been
-%  referred to as the Col\textsubscript{h} thermotropic
-%  phase\cite{feng_scalable_2014}. Q\textsubscript{I}-phase membranes consist of
-%  a tortuous network of three dimensionally interconnected pores that prevent
-%  optimal through-plane transport. In contrast, the densely packed, non-tortuous
-%  and uniform sized pores of H\textsubscript{II}-phase membranes represent the
-%  ideal geometry for achieving high solute
-%  flux\cite{matyka_tortuosity-porosity_2008}. However, the hexagonally packed LC
-%  domains of the H\textsubscript{II}-phase generally form mutually unaligned
-%  domains, which hurts membrane permeability. This domain scale misalignment had
-%  inhibited further development of this technology, and research efforts were
-%  focused on the Q\textsubscript{I} phase, whose geometry does not require
-%  alignment~\cite{zhou_new_2007}. 
-%
-%  However, recently researchers have learned how to macroscopically align the
-%  hexagonal domains which has revived research into H\textsubscript{II}-phase LLC
-%  polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
-%  domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
-%  with subsequent cross-linking to lock the structure in
-%  place\cite{feng_scalable_2014}. In 2016, Feng et al.~showed that one could
-%  also obtain the same result by confining the neat monomer between PDMS or glass
-%  substrates since hexagonal mesophases preferentially anchor perpendicular to
-%  both surfaces\cite{feng_thin_2016}. Current experimental efforts are focused
-%  on extending the method to the H\textsubscript{II} phase and characterizing
-%  the performance of these newly aligned systems.
-%
-%  \begin{figure}
-%	\centering
-%	\begin{subfigure}{.3\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{NaGA3C11.pdf}
-%		\caption{}~\label{fig:monomer}
-%	\end{subfigure}
-%	\begin{subfigure}{.3\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
-%		\caption{}~\label{fig:atomistic_monomer}
-%	\end{subfigure}
-%	\begin{subfigure}{0.3\linewidth}
-%		\centering
-%		\includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
-%		\caption{}~\label{fig:wedge}
-%	\end{subfigure}
-%		\begin{subfigure}{0.4\linewidth}
-%		\centering
-%		\includegraphics[width=0.6\textwidth]{columns.pdf}
-%		\caption{}~\label{fig:wedge_layer}
-%	\end{subfigure}
-%	\begin{subfigure}{0.4\linewidth}
-%		\centering
-%		\includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
-%		\caption{}~\label{fig:hex_packing_simple}
-%	\end{subfigure}
-%	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
-%	exhibits wedge-like character. (d) Monomers stack on top of each other to
-%	create columns with short range order, then assemble into pores with 
-%	hydrophilic head groups (blue) facing towards the pore center. (e) The 
-%	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
-%  \end{figure}
 
@@
   (Figure~\ref{fig:rspots}). In some patterns, the spots are not easily
-  discernable due to obstruction by other features. In that case, we report the
+  discernible due to obstruction by other features. In that case, we report the
   average intensity at the intersection of R-alkanes with the $q_z$ value of
@@
   monomers in a tilted initial configuration, monomers quickly reduced their tilt
-  relative to the $xy$ plane to an angle statisically indistinguishable from zero
+  relative to the $xy$ plane to an angle statistically indistinguishable from zero
   (see Section \ref{S-section:tail_tilt} of Appendix A).
@@
   similar radial distribution functions characterized by a gradual radial
-  transition from a dense hydrophlic core to hydrophobic tails. This observation
+  transition from a dense hydrophilic core to hydrophobic tails. This observation
   enables us to study new systems that have not been experimentally characterized

### 2020-04-27 Ben_Manuscripts/thesis/structure_si.tex
Updates to outline and minor changes to figures
spell checking and mod to usage of subdiffusion

@@
-\chapter{Test}
+\chapter{Supporting Information to Chapter 2}
 
@@
   \texttt{/analysis/Ionic\_Conductivity.py} & \ref{method:ionic_conductivity} & Calculate the 
-  ionic conductivity using the Nernst-Einsten relationship and collective diffusion model. \\ \hline
+  ionic conductivity using the Nernst-Einstein relationship and collective diffusion model. \\ \hline
 
@@
 
-  Crosslinking of the the monomer Na-GA3C11 occurs via a UV initiated free
+  Cross-linking of the the monomer Na-GA3C11 occurs via a UV initiated free
   radical polymerization (FRP) (Figure~\ref{S-fig:xlink_mech}). Head-to-tail addition
@@
 	  radicals react with the vinyl groups of other monomers in order to propagate
-	  crosslinking.}\label{S-fig:xlink_mech}
+	  cross-linking.}\label{S-fig:xlink_mech}
   \end{figure}
@@
         plotted the distribution. There are distinct peaks ca. $-60\degree$, $0\degree$ and
-        $60\degree$ which is indicitive of hexagonal packing. (c) We repeated the 
+        $60\degree$ which is indicative of hexagonal packing. (c) We repeated the 
         same procedure outlined in (a) and (b) with the tail-middles. There is still 
@@
   the trajectory which gives rise to the feature (Figure~\ref{S-fig:rdouble_water_removed}). 
-  We quantified the occurence of pairing interactions by binning the $z$-positions of the center of mass of 
+  We quantified the occurrence of pairing interactions by binning the $z$-positions of the center of mass of 
   the monomer head groups into 20 bins, the same number as the monomers per column. 
@@
   \caption{There are minor differences between the physical properties of a
-  crosslinked (xlink) system versus an uncrosslinked system. The sandwiched configuration (S)
+  cross-linked (xlink) system versus an uncross-linked system. The sandwiched configuration (S)
   exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)

### 2020-04-27 Ben_Manuscripts/thesis/transport.tex
spell checking and mod to usage of subdiffusion

@@
   \section{Introduction}
-
-%  Membranes capable of separating nm-sized solutes with high selectivity and
-%  permeability are highly desirable for a number of applications. For example,
-%  separation of salt from seawater or other briny sources can yield potable
-%  drinking water.~\cite{fritzmann_state---art_2007} Removal of organic
-%  micropollutants, such as personal care products, pesticides and
-%  pharmaceuticals, from surface and groundwaters, can have large benefits for
-%  public health.~\cite{schwarzenbach_challenge_2006} Finally, one can purify and
-%  recover dissolved species present in complex hydraulic fracturing flowback
-%  water waste streams which would help mitigate the effects of deep well
-%  injection and can be sold for profit.~\cite{dischinger_application_2017} 
-%
-%  All of these separations are possible in part with current commercial
-%  membrane separation techniques, but all still suffer from serious drawbacks.
-%  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial
-%  membrane separations of small molecules.~\cite{warsinger_review_2018} RO
-%  membranes are typically dense polymer matrices that separate solutes based on
-%  differences in their solubility and permeability in the membrane
-%  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
-%  selective separations, high feed pressures and thus large amounts of energy are
-%  necessary in order to generate a useful permeate
-%  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
-%  nm-sized pores which can give the same permeate flux as RO with lower applied
-%  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
-%  size, limiting their selectivity.~\cite{werber_materials_2016}.
-%
-%  Under the right conditions, amphiphilic molecules can self-assemble into
-%  ordered nanostructures that may be capable of performing highly selective
-%  separations with permeabilities comparable to
-%  NF.~\cite{alexandridis_amphiphilic_2000} The uniform-sized aqueous pores
-%  characteristic of these types of systems enforce a molecular-size cut-off,
-%  eliminating issues related to the polydisperity of NF
-%  pores.~\cite{zhou_supported_2005} In addition to size-exclusion, it may be
-%  possible to control the chemical environment within the nanopores by altering
-%  the identities of the hydrophilic moieties that form the pores, affording
-%  solute-specific separations.~\cite{dischinger_effect_2017}
-%
-%  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
-%  bicontinuous cubic (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
-%  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010}
-%  When cross-linked, these materials can function as mechanically strong
-%  separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} phase
-%  has hexagonally packed, straight pores which is the ideal geometry for high
-%  throughtput separations. However, the synthesis of H\textsubscript{II}
-%  membranes with highly aligned hexagonal mesophases has been a challenge that
-%  has been met with limited success and has prevented the material's viability as
-%  a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The
-%  Q\textsubscript{I} phase consists of a three dimensional network of tortuous
-%  and interconnected pores.  It's more facile synthesis has yielded it more
-%  success. The latest Q\textsubscript{I} phase membranes have been shown to
-%  exhibit selectivities higher than commercial NF and RO membranes with permeabilities
-%  higher than commercial RO membranes.~\cite{dischinger_application_2017}
-%
-%  Although Q\textsubscript{I} membranes have shown promising results, it
-%  is not clear how to controllably design them for specific separations
-%  beyond what has already been achieved. Dischinger et al. found that they
-%  do not separate purely on the basis of size. Empirical modeling revealed
-%  correlations between various solute physicochemical properties and 
-%  observed solute rejection. Although there was some agreement with their
-%  empirical model, it does not offer a sufficiently detailed explanation
-%  of governing molecular interactions.~\cite{dischinger_effect_2017}
 
@@
   In the remainder of the paper, we describe and quantify three trapping 
-  mechanisms which give rise to subdiffusive solute transport behavior. 
+  mechanisms which give rise to subdiffusive solute transport behavior
+  %BJCF: added
+  on timescales of hundreds of nanoseconds. 
   We describe the differences in solute motion, specifically their mean
@@
   tails in addition to a water reservoir between periodic images. We filled the
-  pores of our initial configuraiton with water by running the GROMACS command
+  pores of our initial configuration with water by running the GROMACS command
   \texttt{gmx solvate} on our initial configuration followed by the removal of
@@
   We fixed the length of each simulated trajectory so that we could compare the total
-  MSD between different solutes without the influence of the ageing phenomenon.
+  MSD between different solutes without the influence of the aging phenomenon.
   In systems such as ours where solutes show hopping behavior between long periods 
-  of immobility, ageing is defined by the tendency of the average slope of an MSD 
+  of immobility, aging is defined by the tendency of the average slope of an MSD 
   curve to decrease as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
@@
   time or trajectory length is increased, lowering the average MSD. Because the solute 
-  MSDs are non-linear and because of the ageing phenomenon, we did not attempt to calculate
+  MSDs are non-linear and because of the aging phenomenon, we did not attempt to calculate
   a diffusion constant as one might for a Brownian particle with a linear MSD. Instead,
@@
   between subdiffusive, Brownian and superdiffusive MSDs. As a lower bound to our
-  appoximation, we also plotted the uncorrected version of
+  approximation, we also plotted the uncorrected version of
   Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the
@@
   \end{subfigure}
-  \caption{All solutes show subdiffusive transport behavior inside the membrane's
+  \caption{
+  On the timescales simulated in our study, %<-- BJCF: added
+  all solutes show subdiffusive transport behavior inside the membrane's
   nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
@@
   (b) The time-averaged MSD of ethanol is sublinear which suggests transport is
-  governed by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
+  governed by an anomalous subdiffusion process
+  %BJCF: added
+  on the hundreds of nanoseconds timescales simulated in this study  
+  .}\label{fig:qualitative_mechanisms}
   \end{figure}
@@
 
-  Our work demonstrates that there are important, atomistic features of nanostructed, 
+  Our work demonstrates that there are important, atomistic features of nanostructured, 
   self-assembled materials that molecular simulation can play a key role in elucidating.

### 2020-04-27 Ben_Manuscripts/thesis/transport_si.tex
Updates to outline and minor changes to figures
spell checking and mod to usage of subdiffusion

@@
-chapter{Supporting Information to Chapter 3}\label{SI:ch3}
+\chapter{Supporting Information to Chapter 3}\label{SI:ch3}
 
@@
     \item The number of multiple-hydrogen-bond interactions increases.
-    \item On average, propylene glcyol participates in more hydrogen bond interactions than 
+    \item On average, propylene glycol participates in more hydrogen bond interactions than 
     ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)

### 2020-04-28 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
JCTC cover letter, emphasizing methods.

--- 2020-04-27 Ben_Manuscripts/stochastic_transport/cover_letter_JPCB.tex
@@
 
-	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael R.
-	Shirts, for consideration for publication as an Article in the Journal of 
-	Physical Chemistry B. We expect this work to be of significant interest to 
-	researchers who study complex transport in both structured and amorphous 
-	soft materials. Please note that this article has been uploaded to arXiv with
+	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia
+        and Michael R.  Shirts, for consideration for publication as
+        an Article in the Journal of Chemical Theory and
+        Computation. We expect this work to be of significant interest
+        to researchers who study complex transport at the molecular
+        level by adding important new techniques for estimating long
+        time scale behavior, inferring mechanisms, and estimating bulk
+        transport behavior from molecular trajectories. Please note that this article has been uploaded to arXiv with
 	differences only in formatting: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\
 
-	In this article, we use solute trajectories generated from 5$\mu$s molecular
-	dynamics (MD) simulations of an inverted hexagonal (H\textsubscript{II}) phase
-	self-assembled lyotropic liquid crystal (LLC) polymer membrane in order to 
-	parameterize two different stochastic time series models capable of predicting
-	solute flux and selectivity on a macroscopic scale. Realizations of both models
-	quantitatively reproduce the mean squared displacements (MSDs) exhibited by 
-	solutes in MD simulations. This is among the first studies to apply time 
-	series modeling of molecular simulations in order to predict bulk materials properties.\\
+	In this article, we analyze solute trajectories generated from
+        5$\mu$s molecular dynamics (MD) simulations of an inverted
+        hexagonal (H\textsubscript{II}) phase self-assembled lyotropic
+        liquid crystal (LLC) polymer membrane to parameterize two
+        different stochastic time series approaches capable of
+        predicting solute flux and selectivity on a macroscopic
+        scale. Both approaches quantitatively reproduce the mean
+        squared displacements (MSDs) exhibited by solutes in MD
+        simulations. This is among the first studies to apply time
+        series modeling of molecular simulations in order to infer
+        mechanisms, propagate behavior to long time scaless and,
+        estimate bulk materials properties.\\
 
-	This article builds on recent work of ours also published in J. Phys. Chem. B 
-    where we characterized transport mechanisms exhibited by a series of 
-	small polar solutes in an LLC Membrane (Coscia and Shirts \textit{J. Phys.
-	Chem. B}, 123, 6314--6330 (2019)). In that study, we observed subdiffusive solute transport
-	characterized by intermittent hops separated by periods of entrapment. In
-	this work, we build on the chemical intuition gained from our previous study
-	in order to formulate stochastic models which produce trajectory realizations
-	that share the same dynamical properties as those exhibited by solutes in 
-	our MD simulations. We explore two modeling approaches. First, based on the
-	anomalous diffusion literature, we parameterize solute motion as 
-    subordinated fractional Brownian and L\'evy motion processes, based on the observation that 
-	solutes experience a series of dwell times separated by anti-correlated hop
-	lengths. Our second approach adds state-dependent dynamics to standard Markov
-	state modeling approaches. We model solute motion as a series of transitions
-	between various trapped states, each with different dynamical properties.
-	Finally, we demonstrate how one can project our best model onto macroscopic 
-	timescales in order to estimate solute flux and selectivity.\\
+	This article builds on recent work of ours published in
+        J. Phys. Chem. B where we characterized transport mechanisms
+        exhibited by a series of small polar solutes in an LLC
+        Membrane (Coscia and Shirts \textit{J. Phys.  Chem. B}, 123,
+        6314--6330 (2019)). In this work, we build on the chemical
+        intuition gained from our previous study in order to formulate
+        stochastic models which produce trajectory realizations that
+        share the same dynamical properties as those exhibited by
+        solutes in our MD simulations. We explore two main modeling
+        approaches. First, using anomalous diffusion theory, we
+        parameterize solute motion as subordinated fractional Brownian
+        and L\'evy motion processes, based on the observation that
+        solutes experience a series of dwell times separated by
+        anti-correlated hop lengths. Secondly, we add state-dependent
+        dynamics to standard Markov state modeling approaches, where
+        we model solute motion as a series of transitions between
+        various trapped states, each with different dynamical
+        properties.  Finally, we demonstrate how one can project our
+        best model onto macroscopic timescales in order to estimate
+        solute flux and selectivity.\\
 

### 2020-04-28 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
update cover letter.

@@
         level by adding important new techniques for estimating long
-        time scale behavior, inferring mechanisms, and estimating bulk
-        transport behavior from molecular trajectories. Please note that this article has been uploaded to arXiv with
-	differences only in formatting: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\
+        time scale behavior and bulk transport behavior from shorter
+        molecular trajectories exhibiting anomalous diffusion rather
+        than Brownian motion. Please note that this article has been
+        uploaded to arXiv with differences only in formatting:
+        \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\
 
@@
         series modeling of molecular simulations in order to infer
-        mechanisms, propagate behavior to long time scaless and,
-        estimate bulk materials properties.\\
+        propagate behavior to long time scales and estimate bulk
+        materials properties with complex anomalous diffusion
+        mechanisms.\\
 

### 2020-04-28 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
updated abstract.

--- 2020-04-17 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
@@
-\documentclass[journal=jpcbfk,manuscript=article]{achemso}
+\documentclass[journal=jctcce,manuscript=article]{achemso}
 \usepackage{CJK}
@@
 
-  Mathematically modeling complex transport phenomena at the molecular level 
-  can be a powerful tool for identifying transport mechanisms and predicting
-  macroscopic properties. We use two different stochastic time series models,
+  Mathematically modeling complex transport phenomena can be a
+  powerful tool
+  %MRS: this paper doesn't really address identifying transport, though, does it?  Although (other) modeling can be 
+  %MRS: useful, putting it in the abstract implies mechanism identification is in this paper.
+  %for identifying transport mechanisms and predicting
+  %macroscopic properties.  
+  for extracting important physical
+  information from molecular simulation.  In this study, we present
+  two new approaches to use stochastic time series modeling to predict
+  long-time scale behavior and macroscopic properties from molecular
+  simulation which can be generalized to other molecular systems
+  where complex diffusion occurs.
+
+  In this study, we use two different stochastic time series modeling approaches
   parameterized from long molecular dynamics (MD) simulation trajectories of
   a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
-  membrane, in order to predict solute mean squared displacements (MSDs) 
+  membrane in order to predict solute mean squared displacements (MSDs)
   and solute flux, and thus solute selectivity, in macroscopic length pores.
@@
 
-  Next, we generalize Markov state models, treating the
-  configurational states of the system as a Markov process where each
-  state has distinct transport properties. For each state and transition
-  between states, we parameterize the distribution and temporal correlation 
-  structure of positional fluctuations as a means of characterization and to 
-  allow us to predict solute MSDs. We show that both models reasonably reproduce
-  the MSDs calculated from MD simulations. However, qualitative differences 
-  between MD and Markov state dependent model-generated trajectories may limit 
-  its usefulness.
-
-  Finally, we demonstrate how one can use these models to 
-  estimate flux of a solute across a macroscopic-length pore and, based on 
-  those quantities, the membrane's selectivity towards each solute. This work 
-  helps to connect microscopic chemically-dependent solute motions that do not
-  follow simple diffusive behavior with macroscopic membrane performance.
+  Next, we present an approach that generalizes Markov state models,
+  treating the configurational states of the system as a Markov
+  process where each state has distinct transport properties. For each
+  state and transition between states, we parameterize the
+  distribution and temporal correlation structure of positional
+  fluctuations as a means of characterization and to allow us to
+  predict solute MSDs. We show that both models reasonably reproduce
+  the MSDs calculated from MD simulations. However, qualitative
+  differences between MD and Markov state dependent model-generated
+  trajectories may limit its usefulness.
+
+  Finally, we demonstrate how one can use these models to estimate
+  flux of a solute across a macroscopic-length pore and, based on
+  those quantities, the membrane's selectivity towards each
+  solute. This work therefore helps to connect microscopic,
+  chemically-dependent solute motions that do not follow simple
+  diffusive behavior with long-time scale behavior, in an approach
+  generalizable to many kinds of molecular systems with complex dynamics.
 
@@
 
-  \graphicspath{{./figures/arxiv_figures/}}
+  \graphicspath{{./figures/}}
 

### 2020-04-29 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex

@@
         to researchers who study complex transport at the molecular
-        level by adding important new techniques for estimating long
+        level, as it describes important new approaches for estimating long
         time scale behavior and bulk transport behavior from shorter
@@
         series modeling of molecular simulations in order to infer
-        propagate behavior to long time scales and estimate bulk
+        behavior at long time scales and estimate bulk
         materials properties with complex anomalous diffusion
@@
         various trapped states, each with different dynamical
-        properties.  Finally, we demonstrate how one can project our
-        best model onto macroscopic timescales in order to estimate
+        properties.  Finally, we demonstrate how one can project models 
+        onto macroscopic timescales in order to estimate
         solute flux and selectivity.\\

### 2020-04-29 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
Pass at intro and conclusion. Suggestions for shortening

--- 2020-04-17 Ben_Manuscripts/stochastic_transport/Final_Draft_JPCB.tex
@@
 
-  Mathematically modeling complex transport phenomena at the molecular level 
-  can be a powerful tool for identifying transport mechanisms and predicting
-  macroscopic properties. We use two different stochastic time series models,
-  parameterized from long molecular dynamics (MD) simulation trajectories of
-  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
-  membrane, in order to predict solute mean squared displacements (MSDs) 
+  Mathematically modeling complex transport phenomena can be a
+  powerful tool for extracting important physical information from 
+  molecular simulations. In this study, we present two new approaches 
+  that use stochastic time series modeling to predict long-time scale 
+  behavior and macroscopic properties from molecular simulation which
+  can be generalized to other molecular systems where complex diffusion
+  occurs.
+  %BJCA: eliminated repetition and merged paragraphs, since the following is one sentence
+  %In this study, we use two different stochastic time series modeling approaches parameterized 
+  Specifically, we parameterize our models using long molecular dynamics (MD) simulation
+  trajectories of a cross-linked H\textsubscript{II} phase lyotropic liquid
+  crystal (LLC) membrane in order to predict solute mean squared displacements (MSDs)
   and solute flux, and thus solute selectivity, in macroscopic length pores.
@@
 
-  Next, we generalize Markov state models, treating the
-  configurational states of the system as a Markov process where each
-  state has distinct transport properties. For each state and transition
-  between states, we parameterize the distribution and temporal correlation 
-  structure of positional fluctuations as a means of characterization and to 
-  allow us to predict solute MSDs. We show that both models reasonably reproduce
-  the MSDs calculated from MD simulations. However, qualitative differences 
-  between MD and Markov state dependent model-generated trajectories may limit 
-  its usefulness.
-
-  Finally, we demonstrate how one can use these models to 
-  estimate flux of a solute across a macroscopic-length pore and, based on 
-  those quantities, the membrane's selectivity towards each solute. This work 
-  helps to connect microscopic chemically-dependent solute motions that do not
-  follow simple diffusive behavior with macroscopic membrane performance.
+  Next, we present an approach that generalizes Markov state models,
+  treating the configurational states of the system as a Markov
+  process where each state has distinct transport properties. For each
+  state and transition between states, we parameterize the
+  distribution and temporal correlation structure of positional
+  fluctuations as a means of characterization and to allow us to
+  predict solute MSDs. 
+  %BJCA: should we add a pargraph break here? Kind of short, but doesn't quite fit with above
+  We show that both models reasonably reproduce
+  the MSDs calculated from MD simulations. However, qualitative
+  differences between MD and Markov state dependent model-generated
+  trajectories may limit its usefulness.
+
+  Finally, we demonstrate how one can use these models to estimate
+  flux of a solute across a macroscopic-length pore and, based on
+  those quantities, the membrane's selectivity towards each
+  solute. This work therefore helps to connect microscopic,
+  chemically-dependent solute motions that do not follow simple
+  diffusive behavior with long-time scale behavior, in an approach
+  %BJCA: should hyphen in long-time scale be there? I would favor the pronunciation that goes with long time-scale with or w/o the hyphen
+  generalizable to many kinds of molecular systems with complex dynamics.
 
@@
 
-  \graphicspath{{./figures/arxiv_figures/}}
+  \graphicspath{{./figures/}}
 
   \section{Introduction}
+
+  % BJCA: Would it make more sense to have the first paragraph less
+  % applications-focused and more centered around a need for our new methods?
+  % Something like .. 
+  There is a large disparity between the time scales accessible to atomistic
+  molecular dynamics (MD) simulations and experiment.
+  \begin{itemize}
+    \item The dynamics of molecules over nanoseconds of simulation may
+    tell a very different story than that inferred by bulk measurements
+    on the time scale of seconds.
+    %BJCA: can cite something about different diffusive regimes 
+    \item Understanding complex dynamical behavior on short timescales 
+    and connecting them with much longer timescales can provide 
+    fundamental insight which can be used for atomic level design of
+    materials.
+    \item In this work, we pursue this connection applied to highly 
+    selective aqueous filtration membranes and demonstrate how one can
+    gain chemical intuition which serves both theoretical and 
+    experimental researchers.
+  \end{itemize}
 
@@
 
+  % BJCA: I could likely condense this paragraph to focus primarily on the HII phase
+  % and its complex pores.
   Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
@@
   solute-specific separation membranes using the available chemical space of
-  LLC monomers. To date, only a limited subset of LLC monomers have been
+  LLC monomers
+  %BJCA added rest of sentence:
+  by allowing us to understand their macroscopic behavior based on microscopic, chemically-dependent solute motions.
+  To date, only a limited subset of LLC monomers have been
   studied experimentally in membrane applications.
@@
   trajectories per unit cell in order to minimize solute-solute interactions.
-% BJC2: removed this sentence. High uncertainty MSDs don't really relate to long timescale predictions. Unless the MSDs were linear.
-%  This results in relatively high uncertainties in observables such as mean
-%  squared displacement (MSD), preventing reliable long timescale predictions.
   We are in need of an efficient method which can use our limited atomistic 
   simulation data sets in order to predict long timescale solute behavior.
-  %BJC2: following sentence replaced with above
-%  We are in need of a way of studying the collective motion of a much larger
-%  set of solutes over much longer timescales.
-  %MRS11: Maybe this last sentence could be changed. Because you aren't really finding a way to study larger sets of 
-  %solutes over larger timescales, you are using a limited amount of atomistic simulation into long time scale behavior efficiently. We can discuss variations as needed!
-
-  %BJC: maybe this paragraph can be cut down?
+
+  %BJCA: maybe this paragraph can be cut down?
   Mathematical descriptions of transport in complex separations membranes are a
@@
   \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
-  %MRS11: this next sentence could probably be cut - it's kind of vague.
-  %BJC2: True
-%  The complexity of a well-fit model generally parallels the complexity of the
-%  transport mechanism being studied, as well as the transport information the
-%  model conveys. 
   In dense homogeneous membranes, the solution-diffusion model
@@
 
-  %MRS11: in this paragraph, the ``we can'' is vague, and doesn't
-  %ascribe agency.  Is ``We'' our group? Is it the field as whole?
-  %If it's something someone has done in the past, there should be
-  %citations. If it's something that can be done in the future, the
-  %phrasing should be a long the lines of ``it is possible to'', ``it
-  %can be done'', etc.
-
   Using a bottom-up modeling approach, it may be possible to parameterize single
@@
   making long timescale predictions with computational ease and lower
-  uncertainties. Fortunately, there is an abundance of information encoded in
+  uncertainties. 
+  %Fortunately,
+  There is an abundance of information encoded in
   the complex solute trajectories. One can incorporate fluctuations and 
@@
 
-  % BJC: I'd say this is where the intro starts to get technical
-%  We constructed our first model by applying the existing rigorous theoretical
-%  foundation which describes the motion of particles that exhibit non-Brownian,
-%  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
-%  introduced by fractional calculus are instrumental to this
-%  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
-%  normally linear diffusion equation to fractional derivative orders, providing
-%  descriptions of a much more diverse set of behavior, including subdiffusion,
-%  a type of anomalous diffusion exhibited by solutes in this
-%  study.~\cite{klages_anomalous_2008}
-
-  %MRS11: should be clear if first model is previous publications, or what is presented here.
-  %If what is presented here, should talk about how it will be presented, not that it was developed. 
-  %MRS11: research activities happened in the past, presentation of research is described in the present.
-  %or potentially future if describing what will be presented in the rest of the paper. 
-  %BJC: replacement to above.
-  %BJC1: Made clear that this is talking about the first model of this work.
-  %BJC1: went through rest of intro to make sure tense is consistent
-  The first model that we develop in this work allows us to characterize the 
-  hopping and trapping behavior displayed by solutes in our MD simulations. This 
-  type of non-Brownian dynamical behavior results in subdiffusive transport which
-  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
+  % BJCA: resurrected this paragraph
+  We constructed our first model by applying the existing rigorous theoretical
+  foundation which describes the motion of particles that exhibit non-Brownian,
+  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
+  introduced by fractional calculus are instrumental to this
+  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
+  normally linear diffusion equation to fractional derivative orders, providing
+  descriptions of a much more diverse set of behavior, including subdiffusion,
+  a type of anomalous diffusion exhibited by solutes in this on the simulation 
+  time scales of this study.~\cite{klages_anomalous_2008}
+  % BJCA: removing less technical version of above
+%  The first model that we develop in this work allows us to characterize the 
+%  hopping and trapping behavior displayed by solutes in our MD simulations. This 
+%  type of non-Brownian dynamical behavior results in subdiffusive transport which
+%  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
   %MRS12: removing paragraph break
-  % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
-  % stole thesis from paragraph below it
   We treat our system in terms of two well-known classes of anomalous
@@
 
+%BJCA: I could replace above with this, but I think I like the above better. It's more concise.
 %  Three well-known classes of behavior leading to anomalous subdiffusion are
@@
 
+  % BJCA: Is this paragraph needed? 
   Where sufficiently close to observed data, these fitted sFBM models
@@
   hydrogen bonds constrained by the LINCS algorithm. We simulated a time step of 2 fs at
-  a pressure of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and
+  a pressure of 1 bar and 300K controlled by the Parrinello-Rahman barostat and
   the v-rescale thermostat respectively. We recorded frames every 0.5 ns.
@@
 
-  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
+  On the time scales simulated in this study,
+  solutes in this system very clearly exhibit subdiffusive behavior, a type of
   anomalous diffusion. During an anomalous diffusion process, the mean squared 
@@
   we do not simulate enough independent solute trajectories to obtain a reliable
-  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
+  estimate. It is also possible that solute dynamics will become diffusive on
+  long simulation timescales. Therefore, the transition from subdiffusion to regular
+  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD curves. 
+  We can obtain higher precision estimates of $\alpha$ using the dwell
   time distributions described in subsequent sections.
 
+  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
   In this study, we primarily use the MSD as a tool for characterizing the average
@@
   fitting longer time lags to our data is lost in the noise since the analytical values
-  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
+  are so close to zero. Therefore, we obtained $H$ by performing a least squares fit of 
   Equation~\ref{eqn:fbm_autocorrelation} to the first 
@@
 
-%BJC8: from author guidelines. Should there only be a line between column headings?
-%Use a single horizontal rule to separate the column headings from the entries in the table.
-Use horizontal space within the body of the table to separate broad groups of entries.
-Extra vertical space may be used between columns.
-Avoid vertical rules in tables.
-Use lower-case roman letters for footnotes placed at the bottom of a table.
-%MRS9: I'd go with what they said.  Looking at PRE, it looks like you can put double lines above and below the table, though - I added them 
+  %BJCA: I could get rid of this table and define them in text. 
   \begin{table}[!htb]
@@
 
+  %BJCA: maybe this to supporting?
   \begin{figure}
@@
 
+  %BJCA: This section to supporting
   \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}
@@
 
+  % BJCA: could move 2 mode to SI
   \subsubsection{Model predictions}\label{section:AD_all_data}
@@
 
+  %BJCA: potentially move this to SI
   \begin{figure}
@@
 
-  We have tested two different mathematical frameworks for describing solute
-  motion by applying them to an H\textsubscript{II} phase LLC membrane. The
+  We have tested two different mathematical frameworks for
+  %BJCA: rephrase
+  % describing solute motion
+  describing complex solute dynamics
+  by applying them to an H\textsubscript{II} phase LLC membrane. The
   values obtained for the parameters when fitting the models to the time series
@@
   solute is in or out of the pore region allows us to break down individual
-  solute motion into the two distinct regimes and we showed that solute motion
+  solute motion into two distinct regimes and we showed that solute motion
   is clearly restricted while in the tail region. Our Markov state-dependent
@@
   simulations appear to straighten out on long timescales while those predicted
-  AD models continuously curve. This is because pure fractional Brownian motion
-  features hop correlation that persists indefinitely. We may be able to
-  address this by truncating the positional autocorrelation function, allowing
-  correlation to diminish on the 100 ns timescale as suggested by the physical
-  trajectories.
-
-  We demonstrated how one could use the one mode AD model in order to to
+  from the AD models continuously curve. This is because pure fractional Brownian motion
+  features hop correlation that persists indefinitely.
+  However, it is likely that on longer timescales, hops become decorrelated, 
+  causing solute dynamics to transition from subdiffusive to diffusive behavior.
+  We may be able to incorporate this transition by truncating the positional 
+  autocorrelation function, allowing correlation to diminish on the 100 ns 
+  time scale as suggested by the physical trajectories.
+
+  We demonstrated how one could use the one mode AD model,
+  %BJCA: added
+  or any stochastic time series model,
+  in order to to
   determine macroscopic flux and selectivity. We showed that, when using the AD
   model, solute flux decreases with pore length at a rate faster than pure
-  Brownian motion due to anti-correlation between hops. We used the ratio of
-  solute fluxes generated from each model in order to calculate selectivity.
+  Brownian motion due to anti-correlation between hops.
+  % We used the ratio of
+  % solute fluxes generated from each model in order to calculate selectivity.
   Due to differences in hop anti-correlation, we observe length dependent
@@
 
-  Despite their shortcomings, our mathematical models help us think about how
-  to design LLC monomers for solute-specific separations by forcing us to think
-  in terms of controlling solute transport. The anomalous diffusion modeling
-  approach is quite flexible because it does not require knowledge of specific
-  trapping mechanisms. Screening a set of solutes and applying the anomalous
-  diffusion approach can help uncover trapping mechanisms by forcing the
-  scientist to identify features common to solutes with long or short hop
-  lengths and dwell times. 
-  The MSDDM is a powerful way to characterize explicit
-  trapping mechanisms. It clearly partitions a trajectory into discrete
-  mechanisms and quantifies their relative dominance in the real system. For
-  example, it is clear that sodium ion association is primarily responsible for
-  trapping urea while hydrogen bonding dominates ethylene glycol. If one
-  re-designs an LLC monomer to eliminate one source of trapping, then 
-  higher selectivities may result. The modeling approaches presented in this paper 
-  facilitate new ways of approaching complex separation problems.
+%  Despite their shortcomings, our mathematical models help us think about how
+%  to design LLC monomers for solute-specific separations by forcing us to think
+%  in terms of controlling solute transport. The anomalous diffusion modeling
+%  approach is quite flexible because it does not require knowledge of specific
+%  trapping mechanisms. Screening a set of solutes and applying the anomalous
+%  diffusion approach can help uncover trapping mechanisms by forcing the
+%  scientist to identify features common to solutes with long or short hop
+%  lengths and dwell times. The MSDDM is a powerful way to characterize explicit
+%  trapping mechanisms. It clearly partitions a trajectory into discrete
+%  mechanisms and quantifies their relative dominance in the real system. For
+%  example, it is clear that sodium ion association is primarily responsible for
+%  trapping urea while hydrogen bonding dominates ethylene glycol. If one
+%  re-designs an LLC monomer to eliminate one source of trapping, then 
+%  higher selectivities may result. The modeling approaches presented in this paper 
+%  facilitate new ways of approaching complex separation problems.
+
+  % BJCA: Perhaps replace above paragraph with the following:? 
+  In a broader context, it is clear that time series modeling may be a useful way
+  to form a lucid connection between complex solute dynamics on the nanosecond 
+  timescale and macroscopic observables.
+  \begin{itemize}
+    \item On the nanoscopic scale, one can both learn and characterize dynamical
+    modes in order to identify areas of potentially impactful molecular-level design
+    changes. 
+    \item For example, it may be possible to modify solute transport rates and 
+    selectivities in LLC membranes by redesigning the LLC monomers to mitigate or 
+    enhance their chemically dependent interactions with different solutes.
+    \item With these models, dynamics can be propagated onto much longer time 
+    with computational ease.
+    \item This allows one not only to predict a macroscopic observable for a specific
+    system, but to explicitly calculate the effect of perturbations to model parameters
+    that may result from a monomer design change.
+    \item Overall, we hope that this work can advance the reader's understanding of
+    how one can apply time series analysis in order to understand complex diffusive 
+    behavior in any system of interest.
+  \end{itemize}
 

### 2020-04-29 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
Comments on text.

@@
   molecular simulations. In this study, we present two new approaches 
-  that use stochastic time series modeling to predict long-time scale 
+  that use stochastic time series modeling to predict long time-scale 
   behavior and macroscopic properties from molecular simulation which
@@
   occurs.
-  %BJCA: eliminated repetition and merged paragraphs, since the following is one sentence
-  %In this study, we use two different stochastic time series modeling approaches parameterized 
   Specifically, we parameterize our models using long molecular dynamics (MD) simulation
@@
   predict solute MSDs.
-  %BJCA: should we add a pargraph break here? Kind of short, but doesn't quite fit with above
-  We show that both models reasonably reproduce
-  the MSDs calculated from MD simulations. However, qualitative
-  differences between MD and Markov state dependent model-generated
-  trajectories may limit its usefulness.
-
-  Finally, we demonstrate how one can use these models to estimate
-  flux of a solute across a macroscopic-length pore and, based on
-  those quantities, the membrane's selectivity towards each
-  solute. This work therefore helps to connect microscopic,
-  chemically-dependent solute motions that do not follow simple
-  diffusive behavior with long-time scale behavior, in an approach
-  %BJCA: should hyphen in long-time scale be there? I would favor the pronunciation that goes with long time-scale with or w/o the hyphen
-  generalizable to many kinds of molecular systems with complex dynamics.
+
+  %MRS: combined the ``general'' material about models here.  
+  We show that both stochastic models reasonably reproduce the MSDs
+  calculated from MD simulations. However, qualitative differences
+  between MD and Markov state dependent model-generated trajectories
+  may in some cases limit their usefulness. With these parameterized
+  stochastic models, we demonstrate how one can estimate flux of a
+  solute across a macroscopic-length pore and, based on those
+  quantities, the membrane's selectivity towards each solute. This
+  work therefore helps to connect microscopic, chemically-dependent
+  solute motions that do not follow simple diffusive behavior with
+  long time-scale behavior, in an approach generalizable to many types
+  of molecular systems with complex dynamics.
 
@@
 
+  %MRS: agreed.
   % BJCA: Would it make more sense to have the first paragraph less
@@
   % Something like ..
-  There is a large disparity between the time scales accessible to atomistic
-  molecular dynamics (MD) simulations and experiment.
-  \begin{itemize}
-    \item The dynamics of molecules over nanoseconds of simulation may
-    tell a very different story than that inferred by bulk measurements
-    on the time scale of seconds.
-    %BJCA: can cite something about different diffusive regimes 
-    \item Understanding complex dynamical behavior on short timescales 
-    and connecting them with much longer timescales can provide 
+
+There is a large disparity between the time scales accessible to
+atomistic molecular dynamics (MD) simulations and experiment. The
+dynamics of molecules over nanoseconds of simulation may tell a very
+different story than that inferred by bulk measurements on the time
+scale of seconds. Understanding complex dynamical behavior on short
+timescales and connecting them with much longer timescales can provide
 fundamental insight which can be used for atomic level design of
-    materials.
-    \item In this work, we pursue this connection applied to highly 
+materials. In this work, we pursue this connection applied to highly
 selective aqueous filtration membranes and demonstrate how one can
-    gain chemical intuition which serves both theoretical and 
-    experimental researchers.
-  \end{itemize}
+gain chemical intuition which serves both theoretical and experimental
+researchers.
 
@@
   % and its complex pores.
+  %MRS: yes.  QI not relevant
   Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
@@
   %BJCA: maybe this paragraph can be cut down?
+  %MRS: provides context, so OK?
   Mathematical descriptions of transport in complex separations membranes are a
@@
   by long ($\geq 5~\mu$s) MD simulations. 
+  %MRS: moved from below
+  Where sufficiently close to observed data, these fitted models
+  provide a way to propagate information about solute trajectories gathered 
+  at the microsecond time scale to realistic experimental time scales.
 
   % BJCA: resurrected this paragraph
+  % MRS: seems OK.
   We constructed our first model by applying the existing rigorous theoretical
@@
 
+%MRS: more concise better.
 %BJCA: I could replace above with this, but I think I like the above better. It's more concise.
@@
   % BJCA: Is this paragraph needed? 
-  Where sufficiently close to observed data, these fitted sFBM models
-  provide a way to propagate information about solute trajectories gathered 
-  at the microsecond time scale to realistic experimental time scales. 
-  They can also confirm the importance of assumed solute-membrane interactions 
-  used to define the model's functional form, and
-  suggest missing components. They can help researchers formulate hypotheses to
-  explain why a certain set of parameters is characteristic to a specific
-  solute.
+  %MRS: the first sentence is key to the paper thesis and deserves to be emphasized, but I moved it up.
+  %MRS: rest is somewhat redundant.
+  %They can also confirm the importance of assumed solute-membrane interactions 
+  %used to define the model's functional form, and
+  %suggest missing components. They can help researchers formulate hypotheses to
+  %explain why a certain set of parameters is characteristic to a specific
+  %solute.
 
@@
   % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
+  %MRS: good call.
   In this study, we primarily use the MSD as a tool for characterizing the average
@@
   %BJCA: I could get rid of this table and define them in text. 
+  %MRS: eh, tables are a clear way to communicated data, so OK. 
   \begin{table}[!htb]
@@
   %BJCA: maybe this to supporting?
+  %MRS: yeah, I think so. 
   \begin{figure}
@@
   \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}
+  %MRS: yes, though report the results in main text.
 
@@
   % BJCA: could move 2 mode to SI
+  %MRS: Which parts specifically?
+Why rationale of 2 mode to SI?
+What parts of the results would be presented in main text?What is the main story?
+(Two model no good, but we tried it, see SI - but that story doesn't seem consistent with the data, they both seem OK)
   \subsubsection{Model predictions}\label{section:AD_all_data}
@@
 
+  %MRS: some of these discussions might belong in the SI, with just the top line information in the main text.
+People don't really care about the details of the individual parameters, just what story that tells.
   \begin{figure}
@@
 
+  %MRS: this paragraph below may be the sort of summary of the models that would
+  %go in the main text, with the details in the SI.
+
   The model parameters for the one and two mode models tell stories about each
@@
   %BJCA: potentially move this to SI
+  %MRS: seems good.  Again, make sure that the conclusions are referenced in the main text. 
   \begin{figure}
@@
   % BJCA: Perhaps replace above paragraph with the following:? 
+  % MRS: agreed!
   In a broader context, it is clear that time series modeling may be a useful way
-  to form a lucid connection between complex solute dynamics on the nanosecond 
+  to form a clear connection between complex solute dynamics on the nanosecond 
   timescale and macroscopic observables.
@@
   the distributions (Equation~\ref{eqn:passage_times}).
-
   This work was supported in part by the ACS Petroleum Research Fund grant

### 2020-04-29 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
More comments.

@@
 
-  %MRS11: Introduction should not really give the answer so far.
-  %Introduction should describe the questions that will be asked, but
-  %not answer them.  That's not what is expected in an intro, it may confuse people (answers should be in the abstract).
-  %MRS11: this next paragraph could use tweaks/cutting the most, but review the previous paragraphs as well.
-  %MRS11: you can think about putting some of these results into conclusion, though - it reads well now, but might be benefited from reemphasizing results if it's currently missing any of this.
-  %BJC2: slight tweaks and removed conclusions from following paragraph. Also went back through previous
-  % paragraphs to look for conclusions.
-
   Finally, we demonstrate how one can use stochastically generated realizations
@@
 
-  %MRS10: A thought going through this - a diagram with a picture of
-  %the molecule pointing to features that promote certain behavior
-  %would be interesting here.  I would suggest waiting until we get
-  %reviews back, though.  You should get this submitted.
-
   Overall, the AD approach does a reasonable job of predicting solute MSDs and
@@
   fit all of the possible transition distributions and because we could not
-  %MRS10: my feeling is (to keep in the back of the mind) that we may be able to add some sort of 
-  %prior to fit the transition distributions. Lots of distributions can be fit with low amounts of data
-  %if one makes enough assumptions about what the functional form of the distribution is. And we could
-  %presumably come up with something reasonable. But that's for another time. 
   correlate emissions coming from different hop distributions. Many

### 2020-04-30 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
moved things to SI

@@
 
-  Mathematically modeling complex transport phenomena can be a
-  powerful tool for extracting important physical information from 
-  molecular simulations. In this study, we present two new approaches 
-  that use stochastic time series modeling to predict long time-scale 
-  behavior and macroscopic properties from molecular simulation which
-  can be generalized to other molecular systems where complex diffusion
-  occurs.
-  Specifically, we parameterize our models using long molecular dynamics (MD) simulation
-  trajectories of a cross-linked H\textsubscript{II} phase lyotropic liquid
-  crystal (LLC) membrane in order to predict solute mean squared displacements (MSDs)
-  and solute flux, and thus solute selectivity, in macroscopic length pores.
+  Mathematically modeling complex transport phenomena can be a powerful tool
+  for extracting important physical information from molecular simulations. 
+  In this study, we present two new approaches that use stochastic time series
+  modeling to predict long time-scale behavior and macroscopic properties 
+  from molecular simulation which can be generalized to other molecular systems
+  where complex diffusion occurs. Specifically, we parameterize our models using
+  long molecular dynamics (MD) simulation trajectories of a cross-linked 
+  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
+  predict solute mean squared displacements (MSDs) and solute flux, and thus 
+  solute selectivity, in macroscopic length pores.
 
@@
   dwell times, hop lengths between dwells and correlation between hops. We 
-  explore two variations of the anomalous diffusion modeling approach. The first variation
-  applies a single set of parameters to the solute displacements and the second
-  applies two sets of parameters based on the solute's radial distance from the
-  closest pore center.
-
-  Next, we present an approach that generalizes Markov state models,
-  treating the configurational states of the system as a Markov
-  process where each state has distinct transport properties. For each
-  state and transition between states, we parameterize the
-  distribution and temporal correlation structure of positional
-  fluctuations as a means of characterization and to allow us to
+  explore two variations of the anomalous diffusion modeling approach. The first 
+  variation applies a single set of parameters to the solute displacements and 
+  the second applies two sets of parameters based on the solute's radial distance
+  from the closest pore center.
+
+  Next, we present an approach that generalizes Markov state models, treating 
+  the configurational states of the system as a Markov process where each 
+  state has distinct transport properties. For each state and transition between
+  states, we parameterize the distribution and temporal correlation structure of
+  positional fluctuations as a means of characterization and to allow us to
   predict solute MSDs.
 
-  %MRS: combined the ``general'' material about models here.  
-  We show that both stochastic models reasonably reproduce the MSDs
-  calculated from MD simulations. However, qualitative differences
-  between MD and Markov state dependent model-generated trajectories
-  may in some cases limit their usefulness. With these parameterized
-  stochastic models, we demonstrate how one can estimate flux of a
-  solute across a macroscopic-length pore and, based on those
-  quantities, the membrane's selectivity towards each solute. This
-  work therefore helps to connect microscopic, chemically-dependent
-  solute motions that do not follow simple diffusive behavior with
-  long time-scale behavior, in an approach generalizable to many types
-  of molecular systems with complex dynamics.
+  We show that both stochastic models reasonably reproduce the MSDs calculated 
+  from MD simulations. However, qualitative differences between MD and Markov 
+  state dependent model-generated trajectories may in some cases limit their 
+  usefulness. With these parameterized stochastic models, we demonstrate how 
+  one can estimate flux of a solute across a macroscopic-length pore and, based
+  on those quantities, the membrane's selectivity towards each solute. This
+  work therefore helps to connect microscopic, chemically-dependent solute 
+  motions that do not follow simple diffusive behavior with long time-scale 
+  behavior, in an approach generalizable to many types of molecular systems 
+  with complex dynamics.
 
@@
 
-  %MRS: agreed.
-  % BJCA: Would it make more sense to have the first paragraph less
-  % applications-focused and more centered around a need for our new methods?
-  % Something like ..
-
-There is a large disparity between the time scales accessible to
-atomistic molecular dynamics (MD) simulations and experiment. The
-dynamics of molecules over nanoseconds of simulation may tell a very
-different story than that inferred by bulk measurements on the time
-scale of seconds. Understanding complex dynamical behavior on short
-timescales and connecting them with much longer timescales can provide
-fundamental insight which can be used for atomic level design of
-materials. In this work, we pursue this connection applied to highly
-selective aqueous filtration membranes and demonstrate how one can
-gain chemical intuition which serves both theoretical and experimental
+  There is a large disparity between the time scales accessible to atomistic 
+  molecular dynamics (MD) simulations and experiment. The dynamics of molecules 
+  over nanoseconds of simulation may tell a very different story than that 
+  inferred by bulk measurements on the time-scale of seconds. Understanding 
+  complex dynamical behavior on short time-scales and connecting them with much
+  longer time-scales can provide fundamental insight which can be used for 
+  atomic level design of materials. In this work, we pursue this connection 
+  applied to highly selective aqueous filtration membranes and demonstrate how
+  one can gain chemical intuition which serves both theoretical and experimental
   researchers.
@@
   potentially harmful organic micropollutants such as fertilizers, pesticides,
-  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} In
-  the materials industry, there is a strong interest in creating breathable
+  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} 
+  %BJCB: could cut this last sentence. It's kind of awkward  
+  In the materials industry, there is a strong interest in creating breathable
   fabrics which selectively allow passage of water
@@
   %MRS: yes.  QI not relevant
+%  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
+%  can be cross-linked into mechanically strong and highly selective nanoporous
+%  membranes.~\cite{gin_polymerized_2008} They may provide a promising
+%  alternative to conventional membrane separation techniques by being selective
+%  based not only on solute size and charge, but on solute chemical
+%  functionality as well.~\cite{dischinger_application_2017} One can tune the
+%  functionality of LLC monomers in order to enhance or weaken specific
+%  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
+%  morphologies of LLC membranes are being actively developed. The inverted
+%  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
+%  pores on the order of 1 nm in size. A perfectly synthesized
+%  H\textsubscript{II} phase has an ideal geometry for high throughput
+%  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
+%  a large scale as required for high permeability has shown limited
+%  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
+%  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
+%  complex pores of the H\textsubscript{II} phase but its geometry consists of a
+%  tortuous network of 3D interconnected pores which do not require
+%  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
+%  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
+%  H\textsubscript{II} phase, it is considerably easier to produce 
+%  at scale.~\cite{hatakeyama_nanoporous_2010}
+
+  %BJCB: removed discussion of Q1 from above paragraph
   Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
@@
   functionality of LLC monomers in order to enhance or weaken specific
-  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
-  morphologies of LLC membranes are being actively developed. The inverted
-  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
-  pores on the order of 1 nm in size. A perfectly synthesized
-  H\textsubscript{II} phase has an ideal geometry for high throughput
-  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
-  a large scale as required for high permeability has shown limited
-  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
-  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
-  complex pores of the H\textsubscript{II} phase but its geometry consists of a
-  tortuous network of 3D interconnected pores which do not require
-  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
-  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
-  H\textsubscript{II} phase, it is considerably easier to produce 
-  at scale.~\cite{hatakeyama_nanoporous_2010}
-
-  Molecular modeling may make it possible to efficiently evaluate
-  solute-specific separation membranes using the available chemical space of
-  LLC monomers
-  %BJCA added rest of sentence:
-  by allowing us to understand their macroscopic behavior based on microscopic, chemically-dependent solute motions.
-  To date, only a limited subset of LLC monomers have been
-  studied experimentally in membrane applications.
-  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
+  solute-membrane interactions.~\cite{dischinger_effect_2017}
+
+  % BJCB: split into two paragraphs  
+  In this work, we study the inverted hexagonal, H\textsubscript{II}, LLC phase. 
+  The H\textsubscript{II} phase has densely packed, uniform-sized pores on the 
+  order of 1 nm in size. A perfectly aligned H\textsubscript{II} phase has 
+  an ideal geometry for high throughput separations.~\cite{feng_scalable_2014,feng_thin_2016}
+  %BJCB: could add a sentence saying that in pracftice, alignment is hard. Not sure if worth acknowledging for this paper.
+
+  Molecular modeling may make it possible to efficiently evaluate solute-specific
+  separation membranes using the available chemical space of LLC monomers by 
+  allowing researchers to understand their macroscopic behavior based on 
+  microscopic, chemically-dependent solute motions. To date, only a limited 
+  subset of H\textsubscript{II} phase-forming LLC monomers have been studied
+  experimentally in membrane applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
   Even within this small subset, they have demonstrated selectivities that
@@
 
-  %BJCA: maybe this paragraph can be cut down?
-  %MRS: provides context, so OK?
   Mathematical descriptions of transport in complex separations membranes are a
@@
   making long timescale predictions with computational ease and lower
-  uncertainties. 
-  %Fortunately,
-  There is an abundance of information encoded in
+  uncertainties. There is an abundance of information encoded in
   the complex solute trajectories. One can incorporate fluctuations and 
@@
   their inputs are parameterized using a substantial amount of data generated
-  by long ($\geq 5~\mu$s) MD simulations. 
-  %MRS: moved from below
-  Where sufficiently close to observed data, these fitted models
-  provide a way to propagate information about solute trajectories gathered 
-  at the microsecond time scale to realistic experimental time scales.
-
-  % BJCA: resurrected this paragraph
-  % MRS: seems OK.
+  by long ($\geq 5~\mu$s) MD simulations. Where sufficiently close to observed data,
+  these fitted models provide a way to propagate information about solute 
+  trajectories gathered at the microsecond time scale to realistic experimental 
+  time scales.
+
   We constructed our first model by applying the existing rigorous theoretical
   foundation which describes the motion of particles that exhibit non-Brownian,
-  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
-  introduced by fractional calculus are instrumental to this
-  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
-  normally linear diffusion equation to fractional derivative orders, providing
-  descriptions of a much more diverse set of behavior, including subdiffusion,
-  a type of anomalous diffusion exhibited by solutes in this on the simulation 
-  time scales of this study.~\cite{klages_anomalous_2008}
-  % BJCA: removing less technical version of above
-%  The first model that we develop in this work allows us to characterize the 
-%  hopping and trapping behavior displayed by solutes in our MD simulations. This 
-%  type of non-Brownian dynamical behavior results in subdiffusive transport which
-%  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
-  %MRS12: removing paragraph break
+  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} 
+  The tools introduced by fractional calculus are instrumental to this 
+  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the normally
+  linear diffusion equation to fractional derivative orders, providing descriptions
+  of a much more diverse set of behavior, including subdiffusion, a type of 
+  anomalous diffusion exhibited by solutes on the simulation time scales of this
+  study.~\cite{klages_anomalous_2008}
+
   We treat our system in terms of two well-known classes of anomalous
@@
 
-%MRS: more concise better.
-%BJCA: I could replace above with this, but I think I like the above better. It's more concise.
-%  Three well-known classes of behavior leading to anomalous subdiffusion are
-%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
-%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
-%  motion are frequently used alone or in combination to describe single
-%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
-%  is characterized by a distribution of hop lengths and dwell times, where
-%  trajectories consist of sequential independent random draws from each
-%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
-%  viscoelastic environments where each jump comes from a Gaussian distribution
-%  but is anti-correlated to its previous
-%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
-%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
-%  dead ends cause anti-correlated
-%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
-
-%  We treated our system as an FBM process subordinate to a CTRW, or
-%  subordinated FBM (sFBM) for short. 
   We fit sFBM models in two ways: First, we parameterize solute motion using
@@
   observed within the pore region versus within the monomer tails.
-
-  % BJCA: Is this paragraph needed? 
-  %MRS: the first sentence is key to the paper thesis and deserves to be emphasized, but I moved it up.
-  %MRS: rest is somewhat redundant.
-  %They can also confirm the importance of assumed solute-membrane interactions 
-  %used to define the model's functional form, and
-  %suggest missing components. They can help researchers formulate hypotheses to
-  %explain why a certain set of parameters is characteristic to a specific
-  %solute.
 
@@
 
-  On the time scales simulated in this study,
-  solutes in this system very clearly exhibit subdiffusive behavior, a type of
-  anomalous diffusion. During an anomalous diffusion process, the mean squared 
-  displacement (MSD) does not grow linearly with time, but instead it follows 
-  a power law of the form: 
+  On the time scales simulated in this study, solutes in this system very 
+  clearly exhibit subdiffusive behavior, a type of anomalous diffusion. 
+  During an anomalous diffusion process, the mean squared displacement (MSD)
+  does not grow linearly with time, but instead it follows a power law of 
+  the form: 
   \begin{equation} 
@@
   long simulation timescales. Therefore, the transition from subdiffusion to regular
-  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD curves. 
-  We can obtain higher precision estimates of $\alpha$ using the dwell
-  time distributions described in subsequent sections.
-
-  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
-  %MRS: good call.
+  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD
+  curves. We can obtain higher precision estimates of $\alpha$ using the dwell
+  time distributions as described in subsequent sections.
+
+  % BJCB: condensed commented out section that follows into this paragraph
   In this study, we primarily use the MSD as a tool for characterizing the average
-  dynamic behavior of solute trajectories. Rather than using them to calculate 
-  diffusion constants or to relate our simulations to experimental measurements, we
-  compare MSDs calculated from MD simulations to those generated from our models 
-  in order to validate those models. Therefore, it is only important that we use a
+  dynamic behavior of solute trajectories. Therefore, it is only important that we use a
   consistent definition for calculating the MSD between modeled trajectories and
-  directly observed MD trajectories.
-
-  One can measure MSD in two ways. The ensemble averaged MSD measures 
-  displacements with respect to a particle's initial position:
-  \begin{equation}
-  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
-  \label{eqn:ensemble_msd}
-  \end{equation}
-  Fits to the ensemble averaged MSD will always reproduce the form of 
-  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
-  displacements over time lag $\tau$: 
+  directly observed MD trajectories. We chose to calculate the time-averaged MSD from 
+  our MD simulations and stochastic models which measures all observed displacements
+  over time lag $\tau$: 
   \begin{equation}
@@
   \end{equation}
-  where T is the length of the trajectory.
-
-  The time averaged and ensemble averaged MSDs will give identical results 
-  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
-  law distribution of trapping times leads to weak ergodicity breaking.
-  In this case, the time-averaged MSD is linear while the ensemble averaged
-  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With
-  power law trapping behavior, the time between hops diverges so there is no 
-  characteristic measurement time scale of solute motion. In fact, as measurement 
-  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
-  aging, because trajectories with trapping times on the order of the measurement 
-  time get incorporated into the calculation.~\cite{bel_weak_2005}
-
-  We chose to use just the time-averaged MSD to compare MD trajectories with
-  modeled trajectories, because, compared to the ensemble average, it is a more
-  statistically robust measure of the average distance a solute travels over
-  time. The ensemble MSD of only 24 solute trajectories would have much higher
-  uncertainties.
+  where T is the length of the trajectory. In some situations, it may make
+  more sense to use the ensemble MSD. We present further discussion of this
+  choice in Section~\ref{S-section:msd} of the Supporting Information.
+
+  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
+  % MRS: good call.
+
+%  In this study, we primarily use the MSD as a tool for characterizing the average
+%  dynamic behavior of solute trajectories. Rather than using them to calculate 
+%  diffusion constants or to relate our simulations to experimental measurements, we
+%  compare MSDs calculated from MD simulations to those generated from our models 
+%  in order to validate those models. Therefore, it is only important that we use a
+%  consistent definition for calculating the MSD between modeled trajectories and
+%  directly observed MD trajectories.
+%
+%  One can measure MSD in two ways. The ensemble averaged MSD measures 
+%  displacements with respect to a particle's initial position:
+%  \begin{equation}
+%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
+%  \label{eqn:ensemble_msd}
+%  \end{equation}
+%  Fits to the ensemble averaged MSD will always reproduce the form of 
+%  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
+%  displacements over time lag $\tau$: 
+%  \begin{equation}
+%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
+%  \label{eqn:tamsd}
+%  \end{equation}
+%  where T is the length of the trajectory. 
+%  
+%  The time averaged and ensemble averaged MSDs will give identical results 
+%  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
+%  law distribution of trapping times leads to weak ergodicity breaking.
+%  In this case, the time-averaged MSD is linear while the ensemble averaged
+%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With
+%  power law trapping behavior, the time between hops diverges so there is no 
+%  characteristic measurement time scale of solute motion. In fact, as measurement 
+%  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
+%  aging, because trajectories with trapping times on the order of the measurement 
+%  time get incorporated into the calculation.~\cite{bel_weak_2005}
+%  
+%  We chose to use just the time-averaged MSD to compare MD trajectories with
+%  modeled trajectories, because, compared to the ensemble average, it is a more
+%  statistically robust measure of the average distance a solute travels over
+%  time. The ensemble MSD of only 24 solute trajectories would have much higher
+%  uncertainties.
 
@@
 
-  %BJCA: I could get rid of this table and define them in text. 
-  %MRS: eh, tables are a clear way to communicated data, so OK. 
   \begin{table}[!htb]
@@
   distribution of dwell times are both characteristic of CTRWs
-  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}).  The
-  apparent anti-correlation between hops suggests a fractional diffusion
-  process is subordinate to the CTRW. Of the different models, a process
-  subordinated by FBM or FLM is best supported by the data because the
-  analytical correlation structures of hop lengths are close to those observed
-  in our simulations (Figure~\ref{fig:hop_acf}). Fractional motion is common
-  in crowded viscoelastic environments where motion is highly influenced by
-  the movement of surrounding components, such as monomer tails in our
-  case.~\cite{ernst_fractional_2012}
+  (See Figures~\ref{S-fig:hop_distribution_comparison} and~\ref{S-fig:powerlaw}
+  of the Supporting Information). 
+  %The apparent
+  Anti-correlation between hops suggests a fractional diffusion process is 
+  subordinate to the CTRW. Of the different models, a process subordinated by 
+  FBM or FLM is best supported by the data because the analytical correlation 
+  structures of hop lengths are close to those observed in our simulations 
+  (See Figure~\ref{S-fig:hop_acf} of the Supporting Information). Fractional 
+  motion is common in crowded viscoelastic environments where motion is highly
+  influenced by the movement of surrounding components, such as monomer tails 
+  in our case.~\cite{ernst_fractional_2012}
 
@@
 
-  %BJCA: maybe this to supporting?
-  %MRS: yeah, I think so. 
-  \begin{figure}
-  \centering
-  % Next 3: /figures/sfbm_distributions
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
-  \caption{}\label{fig:hop_distribution_comparison}
-  \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
-  \caption{}\label{fig:powerlaw}
-  \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
-  \caption{}\label{fig:hop_acf}
-  \end{subfigure}
-  \caption{Using urea as an example, (a) the distribution of hop lengths can be
-	  fit by a Gaussian in addition to a more general L\'evy stable
-	  distribution, though the L\'evy stable distribution does a better job of
-	  capturing the heavier tails and increased density near 0. We explore
-	  models fit to both distributions, as Gaussian hops are more convenient
-	  to model. (b) The distribution of dwell times is fit well by a power
-	  law but it over-estimates the probability density at long dwell
-	  times. A power law truncated with an exponential cut-off better
-	  describes the probability of long dwell times in our simulations. (c)
-	  The hops are negatively correlated to their previous hop. In
-	  combination, (a) -- (c) support modeling solutes as either
-	  subordinated fractional Brownian or L\'evy motion. All other solutes
-	  show similar distributions and autocorrelation functions (see
-	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
-  }\label{fig:anticorrelated_hops}
-  \end{figure}
+%  %BJCA: maybe this to supporting?
+%  %MRS: yeah, I think so. 
+%  \begin{figure}
+%  \centering
+%  % Next 3: /figures/sfbm_distributions
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
+%  \caption{}\label{fig:hop_distribution_comparison}
+%  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
+%  \caption{}\label{fig:powerlaw}
+%  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
+%  \caption{}\label{fig:hop_acf}
+%  \end{subfigure}
+%  \caption{Using urea as an example, (a) the distribution of hop lengths can be
+%	  fit by a Gaussian in addition to a more general L\'evy stable
+%	  distribution, though the L\'evy stable distribution does a better job of
+%	  capturing the heavier tails and increased density near 0. We explore
+%	  models fit to both distributions, as Gaussian hops are more convenient
+%	  to model. (b) The distribution of dwell times is fit well by a power
+%	  law but it over-estimates the probability density at long dwell
+%	  times. A power law truncated with an exponential cut-off better
+%	  describes the probability of long dwell times in our simulations. (c)
+%	  The hops are negatively correlated to their previous hop. In
+%	  combination, (a) -- (c) support modeling solutes as either
+%	  subordinated fractional Brownian or L\'evy motion. All other solutes
+%	  show similar distributions and autocorrelation functions (see
+%	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
+%  }\label{fig:anticorrelated_hops}
+%  \end{figure}
 
@@
   distribution. We plotted the MLE fits of both on top of urea's hop length
-  distribution in Figure~\ref{fig:hop_distribution_comparison}. The L\'evy
-  distribution does a better job capturing the somewhat heavy tails and high
-  density near 0 of the hop length distribution. However, since there are no
-  known exact simulation techniques for generating realizations of fractional
-  L\'evy motion, this more general fit may not be worthwhile. In fact, we
-  typically observe very little difference between model predictions
-  parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).
+  distribution in Figure~\ref{S-fig:hop_distribution_comparison} of the
+  Supporting Information. The L\'evy distribution does a better job capturing
+  the somewhat heavy tails and high density near 0 of the hop length distribution. 
+  However, since there are no known exact simulation techniques for generating 
+  realizations of fractional L\'evy motion, this more general fit may not be 
+  worthwhile. In fact, we typically observe very little difference between model
+  predictions parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).
 
@@
   approach, we truncate the power law distribution with an exponential cut-off,
-  lowering the probability of extremely long dwell times. We demonstrate this
-  effect in the inset to Figure~\ref{fig:powerlaw}, where the density of the
-  truncated power law drops below that of the pure power law and tends towards
-  0 near a dwell time of 250 ns.
+  lowering the probability of extremely long dwell times. 
+  %We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where 
+  On long time scales, the density of the truncated power law drops below that
+  of the pure power law and tends towards 0 near a dwell time of 250 ns.
 
@@
   %BJCA: This section to supporting
-  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}
-  %MRS: yes, though report the results in main text.
-
-  We observe that in some cases, solute trajectories extracted from our MD
-  simulations display non-stationary behavior. We defined the perceived
-  equilibration time point for each solute based on the time at which the
-  number of solutes inside the pores and tails stabilized
-  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
-  evidence of non-stationary solute behavior after the perceived equilibration
-  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
-  the MSD of the solutes calculated using trajectory data from the first and
-  second halves of the ``equilibrated" simulation time. Ethylene glycol and
-  methanol show considerable differences between the MSDs of the two halves.
-  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
-  shapes of urea and acetic acid's MSD curves are also very similar (see
-  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{|c|c|c|}
-  \hline
-  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
-                           & First Half       & Second Half      \\\hline
-  urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
-  ethylene glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
-  methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
-  acetic acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
-
-  \end{tabular}
-  \caption{In order to be considered stationary, the MSD of the ensemble of
-	  solute trajectories should be the same independent of the portion of
-	  equilibrated trajectory that is analyzed. The MSD values in this
-	  table are averages taken after a 500 ns time lag, calculated
-	  independently from the first and second halves of the equilibrated
-	  solute trajectories. Urea and acetic acid both appear to satisfy the
-	  stationarity criteria, while ethylene glycol and methanol show
-	  significantly smaller MSDs when calculated from the second half of
-	  the equilibrated trajectories.}\label{table:stationarity}
-  \end{table}
-
-  Given stationary data, the AD approach is capable of predicting solute MSDs
-  measured from MD simulations within or near statistical uncertainty. In
-  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized
-  the AD models using the first half of the stationary solute equilibrated
-  trajectories and then compared the model predictions to the MD MSD of the
-  second half of the stationary trajectories. In most cases, the model
-  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.
-
-  This brief analysis suggests that we may be operating on the border of the
-  minimum amount of data required to accurately parameterize AD approach
-  models. Working with only half of the data we collected ($\sim$ 2 $\mu$s
-  post-equilibration) may not always be sufficient for extracting reliable
-  parameter estimates. Therefore, for the remainder of this work, we will
-  employ parameters fit to the entire equilibrated portion of the solute
-  trajectories. Even doubling the data might not be good enough for molecules
-  with statistical non-stationarity, meaning the predictive and interpretive
-  power of the time series modeling applied to these trajectories will be
-  lower.
-
-  % BJCA: could move 2 mode to SI
-  %MRS: Which parts specifically?
-Why rationale of 2 mode to SI?
-What parts of the results would be presented in main text?What is the main story?
-(Two model no good, but we tried it, see SI - but that story doesn't seem consistent with the data, they both seem OK)
+%  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}
+%  %MRS: yes, though report the results in main text.
+%
+%  We observe that in some cases, solute trajectories extracted from our MD
+%  simulations display non-stationary behavior. We defined the perceived
+%  equilibration time point for each solute based on the time at which the
+%  number of solutes inside the pores and tails stabilized
+%  (Figure~\ref{S-fig:equilibration}). With this definition, we observe
+%  evidence of non-stationary solute behavior after the perceived equilibration
+%  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
+%  the MSD of the solutes calculated using trajectory data from the first and
+%  second halves of the ``equilibrated" simulation time. Ethylene glycol and
+%  methanol show considerable differences between the MSDs of the two halves.
+%  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
+%  shapes of urea and acetic acid's MSD curves are also very similar (see
+%  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
+%  
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{|c|c|c|}
+%  \hline
+%  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
+%                           & First Half       & Second Half      \\\hline
+%  urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
+%  ethylene glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
+%  methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
+%  acetic acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
+%
+%  \end{tabular}
+%  \caption{In order to be considered stationary, the MSD of the ensemble of
+%	  solute trajectories should be the same independent of the portion of
+%	  equilibrated trajectory that is analyzed. The MSD values in this
+%	  table are averages taken after a 500 ns time lag, calculated
+%	  independently from the first and second halves of the equilibrated
+%	  solute trajectories. Urea and acetic acid both appear to satisfy the
+%	  stationarity criteria, while ethylene glycol and methanol show
+%	  significantly smaller MSDs when calculated from the second half of
+%	  the equilibrated trajectories.}\label{table:stationarity}
+%  \end{table}
+%
+%  Given stationary data, the AD approach is capable of predicting solute MSDs
+%  measured from MD simulations within or near statistical uncertainty. In
+%  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized
+%  the AD models using the first half of the stationary solute equilibrated
+%  trajectories and then compared the model predictions to the MD MSD of the
+%  second half of the stationary trajectories. In most cases, the model
+%  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.
+%  
+%  This brief analysis suggests that we may be operating on the border of the
+%  minimum amount of data required to accurately parameterize AD approach
+%  models. Working with only half of the data we collected ($\sim$ 2 $\mu$s
+%  post-equilibration) may not always be sufficient for extracting reliable
+%  parameter estimates. Therefore, for the remainder of this work, we will
+%  employ parameters fit to the entire equilibrated portion of the solute
+%  trajectories. Even doubling the data might not be good enough for molecules
+%  with statistical non-stationarity, meaning the predictive and interpretive
+%  power of the time series modeling applied to these trajectories will be
+%  lower.
+
   \subsubsection{Model predictions}\label{section:AD_all_data}
@@
   parameterize AD models with all available data after the perceived
-  equilibration time. The MSD curves generated from both the one and 
-  two mode models are overlaid with the MD simulated MSDs for comparison in
-  Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
-  mode models are presented in Figures~\ref{fig:1mode_parameters}
-  and~\ref{fig:2mode_parameters}.
+  equilibration time.   
+  %BJCB: added next two sentences point towards non-stationarity discussion
+  We observe that in some cases, solute trajectories extracted from our MD
+  simulations may display non-stationary behavior. Our brief analysis 
+  in Section~\ref{S-section:msd_comparison} of the Supporting Information 
+  suggests that we may be operating on the border of the minimum amount of
+  data required to accurately parameterize AD approach models.
+  The MSD curves generated from both the one and two mode models are overlaid
+  with the MD simulated MSDs for comparison in Figure~\ref{fig:anomalous_msds}.
+  The associated parameters for the one and two mode models are presented in
+  Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
 
@@
 People don't really care about the details of the individual parameters, just what story that tells.
+  %BJCB: I think the figures need to stay though   
   \begin{figure}
@@
   cases, both the Brownian (sFBMcut) and L\'evy (sFLMcut) versions of both the
-  one and two mode AD models give very similar results, most likely because
-  their $\alpha_h$ parameter values are relatively close to 2, meaning the hop
-  length distributions are nearly Gaussian even when fit to a more general
-  L\'evy distribution.
-
+  one and two mode AD models give very similar results, 
+  %most likely because
+  %their $\alpha_h$ parameter values are relatively close to 2, meaning
+  because  
+  the hop length distributions are nearly Gaussian even when fit to a more general
+  L\'evy distribution ($\alpha_h \sim 2$).
+
+  % BJCB: I'm not sure I want to move this paragraph because I think the curvature
+  % is important to discuss and I mention its implications in the conclusion
   The deviation between the one mode MSD predictions and MD are primarily due
@@
   However, the modeled trajectories undershoot the mean MD MSD as the time lag
-  increases. As discussed in the previous section, long time positional
-  anti-correlation, on the order of hundreds of ns, may not exist in the MD
-  system. Eventual loss of correlation would result in a shift from sub-linear
-  to linear MSD behavior, as observed in the MD trajectories. Acetic acid
-  exemplifies this point. At first glance, acetic acid's predicted MSD appears
-  to match the curvature of MD quite well, but closer examination reveals that
+  increases. Long time positional anti-correlation, on the order of hundreds of
+  ns, may not exist in the MD system. Eventual loss of correlation would result 
+  in a shift from sub-linear to linear MSD behavior, as observed in the MD 
+  trajectories. Acetic acid exemplifies this point. At first glance, acetic acid's
+  predicted MSD appears to match the curvature of MD quite well, but closer 
+  examination reveals that
   the MD MSD curve may actually shift from a sub-linear to a linear regime around
@@
 
+  % BJCB: I might be able to get away with moving this paragraph to SI if I briefly
+  % mention the reason in the above paragraph.
   The two mode models display curvature more consistent with MD but for
@@
   %go in the main text, with the details in the SI.
-
   The model parameters for the one and two mode models tell stories about each
@@
 
+  %BJCB: maybe move the next two paragraphs to the SI?
   Examining first the parameters of the one mode model, we can begin to break
@@
 
+  % BJCB: I could summarize the four following paragraphs in terms of key
+  % takeaways, like you suggested with the AD model above.
+
   Urea spends the largest fraction of its time trapped via association with
@@
   pronounced than that seen in the hop length distributions of the previous
-  section. We therefore did not consider the Gaussian case (see
-  Figure~\ref{fig:gaussian_levy_comparison}). The correlation structure
-  between hops is consistent with that of FLM (Figure~\ref{fig:msddm_acf}).
-  The parameters of the L\'evy stable distributions along with their Hurst
-  parameters are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated
-  in the Supporting Information, Table~\ref{S-table:msddm_params}).
+  section (see Figure~\ref{S-fig:gaussian_levy_comparison} of the Supporting
+  Information). We therefore did not consider the Gaussian case. The correlation
+  structure between hops is consistent with that of FLM (see 
+  Figure~\ref{S-fig:msddm_acf}). The parameters of the L\'evy stable distributions
+  along with their Hurst parameters are visualized in Figure~\ref{fig:msddm_parameters}
+  (and tabulated in the Supporting Information, Table~\ref{S-table:msddm_params}).
 
@@
   %MRS: seems good.  Again, make sure that the conclusions are referenced in the main text. 
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
-  \caption{}\label{fig:gaussian_levy_comparison}
-  \end{subfigure}
-  % /figures/msddm_acf.py
-  \begin{subfigure}{0.42\textwidth}
-  \includegraphics[width=\textwidth]{msddm_acf.pdf}
-  \caption{}\label{fig:msddm_acf}
-  \end{subfigure}
-  \caption{(a) The emission distributions of hop lengths are non-Gaussian and
-	  heavy-tailed. Shown here is the emission distribution for transitions
-	  between states. The maximum likelihood Gaussian fit severely
-	  underestimates the empirical density of hops near and far from zero
-	  while overestimating the density of hops at intermediate values. (b)
-	  Jumps drawn from the transition distribution are negatively
-	  correlated to each other. The normalized version of
-	  Equation~\ref{eqn:flm_autocovariance} fits well to the data
-	  suggesting FLM is an appropriate way to model jumps.}
-	  \label{fig:msddm_emissions}
-  \end{figure}
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.49\textwidth}
+%  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
+%  \caption{}\label{fig:gaussian_levy_comparison}
+%  \end{subfigure}
+%  % /figures/msddm_acf.py
+%  \begin{subfigure}{0.42\textwidth}
+%  \includegraphics[width=\textwidth]{msddm_acf.pdf}
+%  \caption{}\label{fig:msddm_acf}
+%  \end{subfigure}
+%  \caption{(a) The emission distributions of hop lengths are non-Gaussian and
+%	  heavy-tailed. Shown here is the emission distribution for transitions
+%	  between states. The maximum likelihood Gaussian fit severely
+%	  underestimates the empirical density of hops near and far from zero
+%	  while overestimating the density of hops at intermediate values. (b)
+%	  Jumps drawn from the transition distribution are negatively
+%	  correlated to each other. The normalized version of
+%	  Equation~\ref{eqn:flm_autocovariance} fits well to the data
+%	  suggesting FLM is an appropriate way to model jumps.}
+%	  \label{fig:msddm_emissions}
+%  \end{figure}
 
@@
 
-  % BJCA: Perhaps replace above paragraph with the following:? 
-  % MRS: agreed!
   In a broader context, it is clear that time series modeling may be a useful way
   to form a clear connection between complex solute dynamics on the nanosecond 
-  timescale and macroscopic observables.
-  \begin{itemize}
-    \item On the nanoscopic scale, one can both learn and characterize dynamical
-    modes in order to identify areas of potentially impactful molecular-level design
-    changes. 
-    \item For example, it may be possible to modify solute transport rates and 
-    selectivities in LLC membranes by redesigning the LLC monomers to mitigate or 
-    enhance their chemically dependent interactions with different solutes.
-    \item With these models, dynamics can be propagated onto much longer time 
-    with computational ease.
-    \item This allows one not only to predict a macroscopic observable for a specific
-    system, but to explicitly calculate the effect of perturbations to model parameters
-    that may result from a monomer design change.
-    \item Overall, we hope that this work can advance the reader's understanding of
-    how one can apply time series analysis in order to understand complex diffusive 
-    behavior in any system of interest.
-  \end{itemize}
+  timescale and macroscopic observables. On the nanoscopic scale, one can both 
+  learn and characterize dynamical modes in order to identify areas of potentially
+  impactful molecular-level design changes. For example, it may be possible to 
+  modify solute transport rates and selectivities in LLC membranes by redesigning 
+  the LLC monomers to mitigate or enhance their chemically dependent interactions
+  with different solutes. With these models, dynamics can be propagated onto much 
+  longer time with computational ease. This allows one not only to predict a 
+  macroscopic observable for a specific system, but to explicitly calculate the 
+  effect of perturbations to model parameters that may result from a monomer 
+  design change. Overall, we hope that this work can advance the reader's 
+  understanding of how one can apply time series analysis in order to understand 
+  complex diffusive behavior in any system of interest.
 

### 2020-04-30 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Formatted for JPCB with slight mods to intro
Cover letter for JPCB
moved things to SI

@@
 
-\externaldocument[M-]{Final_Draft}
+\externaldocument[M-]{ms}
 
@@
 
-\title{Supplemental Material: Capturing Subdiffusive Solute Dynamics and 
+\title{Supporting Information: Capturing Subdiffusive Solute Dynamics and 
 Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
@@
   \newpage
+
+  \section{Mean Squared Displacement}\label{section:msd}
+
+  In this study, we primarily use the MSD as a tool for characterizing the average
+  dynamic behavior of solute trajectories. Rather than using them to calculate 
+  diffusion constants or to relate our simulations to experimental measurements, we
+  compare MSDs calculated from MD simulations to those generated from our models 
+  in order to validate those models. Therefore, it is only important that we use a
+  consistent definition for calculating the MSD between modeled trajectories and
+  directly observed MD trajectories.
+
+  One can measure MSD in two ways. The ensemble averaged MSD measures 
+  displacements with respect to a particle's initial position:
+  \begin{equation}
+  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
+  \label{eqn:ensemble_msd}
+  \end{equation}
+  Fits to the ensemble averaged MSD will always reproduce the form of 
+  Equation~\ref{M-eqn:msd_form} of the main text. The time-averaged MSD measures all observed 
+  displacements over time lag $\tau$: 
+  \begin{equation}
+  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
+  \label{eqn:tamsd}
+  \end{equation}
+  where T is the length of the trajectory.
+
+  The time averaged and ensemble averaged MSDs will give identical results 
+  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
+  law distribution of trapping times leads to weak ergodicity breaking.
+  In this case, the time-averaged MSD is linear while the ensemble averaged
+  MSD has the form of Equation~\ref{M-eqn:msd_form} of the main text.~\cite{meroz_toolbox_2015} With
+  power law trapping behavior, the time between hops diverges so there is no 
+  characteristic measurement time scale of solute motion. In fact, as measurement 
+  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
+  aging, because trajectories with trapping times on the order of the measurement 
+  time get incorporated into the calculation.~\cite{bel_weak_2005}
+
+  We chose to use just the time-averaged MSD to compare MD trajectories with
+  modeled trajectories, because, compared to the ensemble average, it is a more
+  statistically robust measure of the average distance a solute travels over
+  time. The ensemble MSD of only 24 solute trajectories would have much higher
+  uncertainties.
 
@@
   \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
+  \caption{}\label{fig:hop_distribution_comparison}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
+  \caption{}\label{fig:powerlaw}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
+  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
+  \caption{}\label{fig:hop_acf}
+  \end{subfigure}
+  \begin{subfigure}{0.3\textwidth}
   \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
@@
   \caption{Hop length distributions, dwell time distributions and hop autocorrelation functions
-  respectively for ethylene glycol (a-c), acetic acid (d-f) and methanol (g-i).
-  See Section~\ref{M-section:AD_parameterization} of the main text for a more detailed discussion.
+  respectively for urea (a-c), ethylene glycol (d-f), acetic acid (g-i), and methanol (j-l).
+  Using urea as an example, (a) the distribution of hop lengths can be fit by a Gaussian in
+  addition to a more general L\'evy stable distribution, though the L\'evy stable distribution
+  does a better job of capturing the heavier tails and increased density near 0. We explore
+  models fit to both distributions, as Gaussian hops are more convenient to model. (b) The 
+  distribution of dwell times is fit well by a power law but it over-estimates the probability
+  density at long dwell times. A power law truncated with an exponential cut-off better
+  describes the probability of long dwell times in our simulations. (c) The hops are negatively
+  correlated to their previous hop. In combination, (a) -- (c) support modeling solutes as either
+  subordinated fractional Brownian or L\'evy motion.
   }\label{fig:anticorrelated_hops}
@@
 
-  We evaluated the predictive capabilities of the AD modeling approach by training
+  We observe that in some cases, solute trajectories extracted from our MD
+  simulations display non-stationary behavior. We defined the perceived
+  equilibration time point for each solute based on the time at which the
+  number of solutes inside the pores and tails stabilized
+  (Figure~\ref{fig:equilibration}). With this definition, we observe
+  evidence of non-stationary solute behavior after the perceived equilibration
+  point, on the $\mu$s timescale.
+
+%  In Table~\ref{table:stationarity}, we compare
+%  the MSD of the solutes calculated using trajectory data from the first and
+%  second halves of the ``equilibrated" simulation time. Ethylene glycol and
+%  methanol show considerable differences between the MSDs of the two halves.
+%  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
+%  shapes of urea and acetic acid's MSD curves are also very similar (see
+%  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
+
+% BJC: This table summarizes the main text
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{|c|c|c|}
+%  \hline
+%  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
+%                           & First Half       & Second Half      \\\hline
+%  urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
+%  ethylene glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
+%  methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
+%  acetic acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
+%
+%  \end{tabular}
+%  \caption{In order to be considered stationary, the MSD of the ensemble of
+%	  solute trajectories should be the same independent of the portion of
+%	  equilibrated trajectory that is analyzed. The MSD values in this
+%	  table are averages taken after a 500 ns time lag, calculated
+%	  independently from the first and second halves of the equilibrated
+%	  solute trajectories. Urea and acetic acid both appear to satisfy the
+%	  stationarity criteria, while ethylene glycol and methanol show
+%	  significantly smaller MSDs when calculated from the second half of
+%	  the equilibrated trajectories.}\label{table:stationarity}
+%  \end{table}
+
+  %We evaluated the predictive capabilities of the AD modeling approach by training
+  We trained
   the model parameters on the first half of the equilibrated MD trajectory data and
-  then comparing the MSD calculated from AD model realizations to the MSD calculated
+  then compared the MSD calculated from AD model realizations to the MSD calculated
   from the second half of the equilibrated MD trajectory data. This metric is
@@
 
+  This brief analysis suggests that we may be operating on the border of the
+  minimum amount of data required to accurately parameterize AD approach
+  models. Working with only half of the data we collected ($\sim$ 2 $\mu$s
+  post-equilibration) may not always be sufficient for extracting reliable
+  parameter estimates. Therefore, in the main text, we employ parameters fit
+  to the entire equilibrated portion of the solute trajectories. Even doubling
+  the data might not be good enough for molecules with statistical 
+  non-stationarity, meaning the predictive and interpretive power of the time
+  series modeling applied to these trajectories will be lower.
+
   \begin{figure}[h]
@@
   intervals of the MD MSD curves generated from the second half of the equilibrated
-  solute data. The models which use pure power laws systematically under-predict
-  the MD MSD curves. Over- and under-estimated curvature of the of urea and acetic acid's 
+  solute data. Over- and under-estimated curvature of the of urea and acetic acid's 
   MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
   under-predicted at long timescales and those of acetic acid to be under-predicted
-  at short timescales. Note that the sFBMcut and sFLMcut models are the same as 
-  those in the main text.}\label{fig:train_test}
+  at short timescales. The models which use pure power laws systematically under-predict
+  the MD MSD curves. 
+  % Note that the sFBMcut and sFLMcut models are the same as those in the main text.
+  }\label{fig:train_test}
   \end{figure}
@@
   \newpage
-  \section{Table of MSDDM parameters}\label{section:msddm_params}
+  \section{MSDDM parameters}\label{section:msddm_params}
+
+  We observe correlated emissions drawn from L\'evy stable distributions. The
+  deviation of the emission distributions from Gaussian behavior is far more
+  pronounced than that seen in the hop length distributions of the AD model.
+  (see Figure~\ref{fig:gaussian_levy_comparison}) We therefore did not consider
+  the Gaussian case for the MSDDM. The correlation structure between hops is 
+  consistent with that of FLM (Figure~\ref{fig:msddm_acf}).
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
+  \caption{}\label{fig:gaussian_levy_comparison}
+  \end{subfigure}
+  % /figures/msddm_acf.py
+  \begin{subfigure}{0.42\textwidth}
+  \includegraphics[width=\textwidth]{msddm_acf.pdf}
+  \caption{}\label{fig:msddm_acf}
+  \end{subfigure}
+  \caption{(a) The emission distributions of hop lengths are non-Gaussian and
+	  heavy-tailed. Shown here is the emission distribution for transitions
+	  between states. The maximum likelihood Gaussian fit severely
+	  underestimates the empirical density of hops near and far from zero
+	  while overestimating the density of hops at intermediate values. (b)
+	  Jumps drawn from the transition distribution are negatively
+	  correlated to each other. The normalized version of
+	  Equation~\ref{M-eqn:flm_autocovariance} fits well to the data
+	  suggesting FLM is an appropriate way to model jumps.}
+	  \label{fig:msddm_emissions}
+  \end{figure}
 

### 2020-04-30 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
moved things to SI

@@
         molecular trajectories exhibiting anomalous diffusion rather
-        than Brownian motion. Please note that this article has been
-        uploaded to arXiv with differences only in formatting:
-        \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\
+        than Brownian motion. Please note that the content of this article
+        %BJC: see if you agree with these changes
+        has been uploaded to arXiv: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}.
+        For submission to JCTC, we have made minor changes to the introduction,
+        abstract and conclusion in order to make it more suited for readers of 
+        the journal. We also made efforts to shorten the manuscript by moving 
+        certain discussions and figures to the supporting information. \\
 

### 2020-04-30 Ben_Manuscripts/thesis/intro.tex
moved things to SI

@@
   Municipal waste-waters are rich in carbon, nitrogen and phosphorus-containing 
-  compounds.~\cite{romero_raw_2013} The recovery of such products, which can be 
-  achieved using selective membranes, has numerous potential uses.\cite{sales_resource_2015}
+  compounds. The recovery of such products, which can be 
+  achieved using selective membranes, has numerous potential uses.\cite{romero_raw_2013,sales_resource_2015}
   For example, nitrogen and phosphorus recovery can help sustain fertilizer 

### 2020-04-30 Ben_Manuscripts/thesis/stochastic_transport.tex
moved things to SI

@@
   continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
-  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
+  random walks on fractals (RWFs). These types of
   motion are frequently used alone or in combination to describe single
-  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
+  particle trajectories.~\cite{meroz_toolbox_2015,metzler_anomalous_2014,morrin_three_2018} A CTRW
   is characterized by a distribution of hop lengths and dwell times, where

### 2020-04-30 Ben_Manuscripts/thesis/thesis.tex
spell checking and mod to usage of subdiffusion
moved things to SI

@@
 \usepackage{graphicx}		% to insert figures
-\usepackage{hyperref}		% PDF hyperreferences??
+%\usepackage{hyperref}		% PDF hyperreferences??
 \usepackage{amsmath}
@@
 
-\reader{Prof. Richard Noble}		%  2nd person to sign thesis
-\readerThree{Prof. Douglas Gin}		%  3rd person to sign thesis
-\readerFour{Prof. Matthew Glaser}
-\readerFive{Prof. Robert Davis}
+\reader{Prof. Matthew Glaser}
 
@@
   design space available for liquid crystal monomer design which may allow one to
-  tailor solute interactions within the membrane pores. Our currrent
-  understanding of these membrane is based primarily on experimental measurements
+  tailor solute interactions within the membrane pores. Our current
+  understanding of these membranes is based primarily on experimental measurements
   and macroscopic modeling which limits our insight and ability to design them 
@@
   number of hidden dynamical modes in multidimensional solute time series. This model
-  offers a flexibile approach to modeling solute motion and helps us to uncover 
+  offers a flexible approach to modeling solute motion and helps us to uncover 
   mechanisms with minimal human effort.
@@
 % \LoFisShort	% use this only for 1-page Table of Figures
-\emptyLoF	% use this if there is no List of Figures
+%\emptyLoF	% use this if there is no List of Figures
 
 % \LoTisShort	% use this only for 1-page Table of Tables
-\emptyLoT	% use this if there is no List of Tables
+% \emptyLoT	% use this if there is no List of Tables
 

### 2020-04-30 Ben_Manuscripts/thesis/transport.tex
moved things to SI

@@
   \centering
-  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
+  \begin{tabular}{ |m{2.5cm}m{1.75cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
     \hline
-    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
+    \multicolumn{2}{|c}{Solute Name~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
     \hline

### 2020-05-01 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Small reference changes and removing unused figs

@@
 
-\externaldocument[M-]{ms}
+\externaldocument[M-]{Final_Draft_JCTC}
 
@@
 
-  Analogous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
   Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the

### 2020-05-02 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
More comments on draft.

@@
   %BJCB: could cut this last sentence. It's kind of awkward  
-  In the materials industry, there is a strong interest in creating breathable
-  fabrics which selectively allow passage of water
-  vapor.~\cite{mondloch_destruction_2015}
+  %MRSB: agree  
+  %In the materials industry, there is a strong interest in creating breathable
+  %fabrics which selectively allow passage of water
+  %vapor.~\cite{mondloch_destruction_2015}
 
@@
   %BJCB: could add a sentence saying that in pracftice, alignment is hard. Not sure if worth acknowledging for this paper.
+  %MRSB: nah, not here.
 
@@
   %BJCB: I think the figures need to stay though   
+  %MRSB: Hmm. I'm not entirely convinced, but we can leave it in for now and see what the reviewers think.
   \begin{figure}
@@
   non-physical reasons. Every time a switch between the pores and tails occurs,
-  the width of the distribution used to model hops changes. We are unaware of
-  an appropriate technique which can correlate hops that come from different
-  hop distributions, therefore every time a mode switch occurs, the correlation
-  structure is broken. Solutes that switch between modes the least show
+  the width of the distribution used to model hops changes, and the correlation structure is broken. 
+  %MRSB: I cut below.
+  %We are unaware of
+  %an appropriate technique which can correlate hops that come from different
+  %hop distribution every time a mode switch occurs, the correlation
+  %structure is broken. 
+  Solutes that switch between modes the least show
   predicted MSDs with the greatest curvature. Due to the much larger
@@
   mode transitions are relatively rare and the predicted MSDs have significant
-  curvature. This artificially solves the problem of long timescale
-  correlation, however we do not recommend this as it has no physical basis.
+  curvature. This artificially resolves the problem of long timescale
+  correlation, however, it has no physical basis.
 
@@
   %BJCB: maybe move the next two paragraphs to the SI?
+  %MRSB: I think that this is more useful in the main text, since it connects models to the simulations and the physics.
   Examining first the parameters of the one mode model, we can begin to break
@@
 
-  Urea spends the largest fraction of its time trapped via association with
+  %MRSB: I think people like the physical intuition gained. I added bullet points to aid reading. 
+  \begin{itemize}
+  \item \textit{Urea} spends the largest fraction of its time trapped via association with
   sodium ions. It does so 31\% of the total time while in the tails (state 3)
@@
 
-  Ethylene glycol spends the largest fraction of its time trapped in a hydrogen
+  \item \textit{Ethylene glycol} spends the largest fraction of its time trapped in a hydrogen
   bonded state. It does so 24\% of the total time while in the tails (state 2)
@@
 
-  Methanol spends most of its time unbound in the tail region (state 1) and
+  \item \textit{Methanol} spends most of its time unbound in the tail region (state 1) and
   spends a significant portion of time hydrogen bonded while in the tail
@@
 
-  Finally, acetic acid spends the majority of its time hydrogen bonding both in
+  \item \textit{Acetic acid} spends the majority of its time hydrogen bonding both in
   and out of the pore (states 2 and 6). Although it has an unshielded carbonyl
@@
   rates to urea given their structural similarity.
+  \end{itemize}
 
@@
 
+  %MRSB: discussion of parameter specifics is a potential place to move.
   \begin{figure}

### 2020-05-07 Ben_Manuscripts/hdphmm/Draft.tex
Filling in missing parts of draft

@@
-\documentclass{article}
+\documentclass[journal=jpcbfk,manuscript=article]{achemso}
 
@@
 \usepackage{subcaption}
-\usepackage[margin=1in]{geometry}
 \usepackage{amsmath} % or simply amstext
@@
 \newcommand{\angstrom}{\textup{\AA}}
-\newcommand{\colormap}{jet}  % colorbar to use
 \usepackage{cleveref}
@@
 \usepackage{xr}
-\usepackage{setspace}
-\doublespacing
 %\DeclareUnicodeCharacter{03C9}{$\omega$}
@@
 \title{Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
-       of Solute Trajectories in Nanostructured Membranes.}
-
-\author{Benjamin J. Coscia, Christopher P. Calderon, Michael R. Shirts}
+       of Solute Trajectories in Nanostructured Membranes}
+\author{Benjamin J. Coscia}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+\author{Christopher P. Calderon}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+\author{Michael R. Shirts}
+\email{michael.shirts@colorado.edu}
+\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
 
@@
 
+  \begin{abstract}
+
+  Appropriate time series modeling of complex diffusion on the microsecond time scale
+  can provide a path towards inferring transport mechanisms and predicting bulk properties
+  characteristic of much longer time scales. In this work we apply the infinite hidden 
+  Markov model (IHMM) to solute center-of-mass trajectories generated from long 
+  molecular dynamics simulations in a cross-linked inverted hexagonal phase lyotropic 
+  liquid crystal (LLC) membrane in order to automatically detect and parameterize an unknown 
+  number of distinct latent vector autoregressive dynamical modes.
+
+  We group similar solute behavior into clusters, analyze the dynamics characteristic
+  to each cluster and relate them to physical interactions between solutes and the 
+  membrane. This enhancement to our understanding of the diverse range of influential 
+  solute-membrane interactions allows us hypothesize design changes to LLC monomers 
+  aimed towards controlling the rates of solute passage, thus improving the selective 
+  performance of LLC membranes.
+
+  Along with parameters of individual states, the IHMM simultaneously infers a transition
+  matrix which allows us to stochastically propagate solute behavior from all of the 
+  independent trajectories onto much longer time scales while still preserving the 
+  qualitative behavior characteristic of the MD trajectories. This affords a direct 
+  connection to important macroscopic observables used to characterize performance like
+  solute flux and selectivity.
+
+  Overall, this work provides an effective way to simultaneously identify transport 
+  mechanisms and project complex diffusive behavior on long time scales.
+
+  \end{abstract}
+
   \section{Introduction}
 
-%  There is a need for highly selective membranes in order to perform efficient 
-%  separations of components of complex aqueous streams.
-%  %MRS2: add some more examples (When you get around to it).
-%  \begin{itemize}
-%    \item Organic micropollutants
-%    \item Desalination and boric acid removal from seawater.
-%    \item While many researchers focus on membrane permeability, we may be 
-%    able to reduce costs of commercial nanofiltration and reverse osmosis with
-%    higher selectivity.~\cite{werber_materials_2016}
-%  \end{itemize}
+  % BJC: Not sure if this should be the first paragraph, or if I could just
+  % delete this paragraph and start with the next one. 
+  There is a need for highly selective membranes in order to perform efficient 
+  separations of the components of complex aqueous streams.
+  \begin{itemize}
+    \item Desalination and boric acid removal from seawater.
+    \item Organic micropollutants
+    \item Hydraulic fracturing flowback water
+    \item Breathable chemical warfare agent barriers
+    \item High purity chemicals
+    \item While many researchers focus on membrane permeability, we may be 
+    able to reduce costs of commercial nanofiltration and reverse osmosis with
+    higher selectivity.~\cite{werber_materials_2016}
+  \end{itemize}
+
+  The ability to efficiently design novel membrane materials for selective separations would be 
+  greatly enhanced by easily interpretable methods for connecting microscopic fluctuations
+  with macroscopic observables.
+  \begin{itemize}
+  	\item If one could apply molecular dynamics (MD) simulations to explain important
+  	experimental metrics such as solute flux and selectivity in terms of detailed 
+  	chemically dependent solute motion, then we can more easily bridge the disconnect
+  	between theory and application.
+  	%BJC: this could potentially be moved further down
+  	\item There are two main challenges associated with this goal.
+  	%since complex and
+  	%diverse diffusive motion on time scales accessible to molecular simulations prevents
+  	%us from easily relating chemically dependent solute motion to experimental time scales.
+  	\item First, we need a simple way to identify and parameterize the fluctuations
+  	characteristic to dominant solute-membrane interactions.
+  	\item Second, we need a way to propagate this behavior far beyond the time scales
+  	afforded by MD.
+  \end{itemize}
+
+  In this work, we are particularly interested in the design of lyotropic liquid crystal (LLC)
+  monomers, a class of amphiphilic molecules whose ordered self-assembled phases can be 
+  cross-linked into mechanically strong membranes capable of highly selective separations.
+  \begin{itemize}
+  	\item Inverted hexagonal, H\textsubscript{II}, phase LLC membranes are characterized
+  	by hexagonally packed, uniform-sized and straight pores, an ideal geometry for high 
+  	throughput transport.
+	\item Their pores are lined with the LLC monomer functional groups which can
+	potentially be designed to interact with solutes in a chemically-specific manner.
+	\item It would be extremely useful to experimentalists if we could connect LLC monomer
+	design with measurable quantities.
+  \end{itemize}
+
+  We have already progressed our understanding of LLC monomer design in our previous work
+  by building stochastic time series models based on the chemical intuition gained
+  from qualitative MD studies of solute transport in an H\textsubscript{II} phase LLC
+  membrane.~\cite{coscia_chemically_2019,coscia_capturing_2020}
+  \begin{itemize}
+    \item We identified three classes of trapping behavior which result in short time scale
+    subdiffusion.
+    \item In our first approach to stochastically model this behavior, we treated the
+    system's dynamics as a sequence of anti-correlated hops between power law distributed
+    periods of entrapment, a framework called subordinated fractional Brownian or L\'evy
+    motion.
+    \item In a second approach, we treated solute motion as a Markov state model with 
+    state-dependent dynamics, where we parameterized the state transition probabilities 
+    between each of eight discrete states, defined by the observed trapping mechanism, 
+    as well as the solute dynamics within each of these states. 
+    \item We showed how one could use realizations of any stochastic model like these in
+    order to predict macroscopic flux and selectivity. 
+  \end{itemize}
+
+  Although powerful and insightful, our previous work required considerable human effort
+  in order to analyze the MD trajectories and to hypothesize stochastic models which
+  matched the behavior of solutes.
+  \begin{itemize}
+    \item It would be significantly more useful and broadly applicable if we could 
+    design an approach which automatically distinguishes and parameterizes varied solute 
+    dynamics and leaves a facile way to generate an ensemble of stochastic trajectory
+    realizations that can be used to predict macroscopic transport properties.
+  \end{itemize}
+
+  In this work we attempt to minimize human effort by applying the infinite hidden 
+  Markov Model (IHMM)~\cite{beal_infinite_2002,calderon_inferring_2015}, a nonparameteric 
+  Bayesian classification technique, in order to automatically detect and infer the 
+  parameters of an unknown number of latent vector autoregressive (VAR) modes present 
+  in solute center-of-mass time series trajectories. 
+  \begin{itemize}
+    \item The IHMM has not been used much for MD trajectory analysis.
+    \item It's been used extensively for speaker diarization and has found some application
+    in single particle trajectory analysis.
+  \end{itemize}
+
+  We aim to address two primary scientific 
+  questions with this work. 
+  %BJC: this may be redundant from the second paragraph. Maybe better suited here?
+  First, we want
+  to know if the IHMM algorithm can help researchers efficiently uncover underlying
+  transport mechanisms which give rise to different solute dynamical behavior.
+  Second, we want to evaluate the ability of our model to reproduce solute trajectories
+  in a stochastic manner so that we can use it to predict macroscopic transport 
+  properties which would otherwise require much longer MD simulations.
+
+  We use the parameters of the states identified by the IHMM in order to infer 
+  dominant solute-membrane interactions and transport mechanisms. We cluster similar 
+  state parameters in order to reduce the state space and to understand which segments 
+  of the solute trajectories exhibit similar behavior. We support our mechanistic 
+  hypotheses via quantitative comparison to various physical membrane properties and
+  solute-membrane interactions.
+
+  Finally, we use the VAR parameters and state transition probability matrix in
+  order to generate stochastic trajectory realizations with behavior similar to that
+  exhibited by MD. 
+  \begin{itemize}  
+    \item One can project these realizations onto much longer timescales with 
+    computational ease and use them to predict macroscopic properties.
+  \end{itemize}
+
+%  Because independent solute trajectories generated by MD simulations share 
+%  similar state dynamics, we can use the IHMM to generate stochastic trajectory 
+%  realizations which sample from all behavior exhibited by MD. We verify that our
+%  stochastic realizations reproduce the expected hopping and trapping behavior 
+%  exhibited by MD. We quantitatively validate these trajectories by comparing 
+%  their mean squared displacement (MSD) to those measured by MD.
+
 %
@@
 %%  \end{itemize}
-%
-%  Lyotropic liquid crystals (LLC) are a class of amphiphilic molecules whose ordered phases
-%  can be cross-linked into mechanically strong membranes capable of highly selective
-%  separations.
-%  \begin{itemize}
-%    \item The shape of the LLC monomers and water content dictates the ordered phase 
-%    that they form. There are two phases of particular interest for membrane applications.
-%  	\item H\textsubscript{II} phase lyotropic liquid crystals are characterized by 
-%  	hexagonally packed, straight, pores while the Q\textsubscript{I} phase consists of
-%  	a tortuous network of 3D interconnected pores. 
-%  	\item In both cases the pores are uniform in size with radii on the order of 1 nm
-%    %MRS2: is it really a molecular weight cutoff?
-%    %BJC2: is molecular size better? Obviously there are other factors like shape, but I don't want to get into that
-%  	giving them a very strict molecular size cut-off.
-%	\item Additionally, they have the potential to disrupt conventional membrane separation
-%	techniques by being selective based not only on size and charge, but on chemical
-%	functionality as well.
-%	\item Their pores are lined with LLC monomer functional groups which can potentially
-%	be designed to interact with solutes in a chemically-specific manner
-%  \end{itemize}
 %
@@
 
-  %%%%%%%%%%%%%%%%%%%%%%%% Thesis chapter starts here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-  In our previous study, we designed two different approaches which used
-  solute time series in order to parameterize stochastic models that could be used
-  to project transport on much longer timescales. In our first approach we modeled 
-  solute trajectories as subordinated fractional Brownian and L\'evy motion, called
-  the anomalous diffusion (AD) model. We generated solute trajectories by generating
-  a series of anti-correlated hops separated by random periods of entrapment drawn 
-  from a power law distribution. Our second approach treated solute motion as a Markov
-  state model with state-dependent dynamics, called the Markov state-dependent dynamical
-  model (MSDDM). We parameterized the state transition probabilities between
-  each of eight discrete states as well as the solute dynamics within each of these
-  states. We generated stochastic trajectory realizations by drawing a state
-  sequence based on the transition probability matrix and incorporating the state dynamics
-  while solutes were trapped in each state.
-
-  Although both models had reasonable success at predicting solute mean squared 
-  displacements (MSDs) on MD simulation timescales, they had shortcomings.
-  The MSDDM failed to reproduce the hopping and trapping behavior that
-  characterizes solute center-of-mass trajectories in our MD simulations.
-  The AD model did not suffer this qualitative shortcoming, but the persistent 
-  curvature of the predicted MSD curves suggested that the model might 
-  underestimate MSDs on long timescales. The formulation of both models required
-  careful examination and characterization of the interactions and dynamics exhibit
-  by MD trajectories which required considerable human effort.
-
-  In this work we attempt to minimize human effort by applying the infinite hidden 
-  Markov Model (IHMM)~\cite{beal_infinite_2002,calderon_inferring_2015}, a nonparameteric 
-  Bayesian classification technique, in order to automatically detect and infer the 
-  parameters of an unknown number of latent autoregressive (AR) modes present in solute
-  center-of-mass time series trajectories.
-  We aim to address two primary scientific questions with this work. First, we want
-  to know if the IHMM algorithm can help researchers efficiently uncover underlying
-  transport mechanisms which give rise to different solute dynamical behavior.
-  Second, we want to evaluate the ability of our model to reproduce solute trajectories
-  in a stochastic manner so that we can use it to predict macroscopic transport 
-  properties which would otherwise require much longer MD simulations.
-
-  We use the parameters of the states identified by the IHMM in order to infer 
-  dominant solute-membrane interactions and transport mechanisms. We cluster similar 
-  state parameters in order to reduce the state space and to understand which segments 
-  of the solute trajectories exhibit similar behavior. We support our mechanistic 
-  hypotheses via quantitative comparison to various physical membrane properties and
-  solute-membrane interactions.
-
-  Because independent solute trajectories generated by MD simulations share 
-  similar state dynamics, we can use the IHMM to generate stochastic trajectory 
-  realizations which sample from all behavior exhibited by MD. We verify that our
-  stochastic realizations reproduce the expected hopping and trapping behavior 
-  exhibited by MD. We quantitatively validate these trajectories by comparing 
-  their mean squared displacement (MSD) to those measured by MD.
-
   \section{Methods}
@@
   ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}  
-  Our python implementation of the IHMM algorithm is available online at 
+  Our python implementation of the IHMM algorithm is available online at \\
   \texttt{https://github.com/bencoscia/hdphmm}. All other post-simulation 
-  trajectory analysis tools are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
+  trajectory analysis tools are available online at
+  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
 
@@
 
-  %Based on the algorithms developed by Fox et al.~\cite{fox_sticky_2007}, 
-  Using the IHMM framework, we estimated the most likely number and sequence of hidden
-  states in each solute center-of-mass trajectory while simultaneously inferring VAR(1)
+  Using the IHMM framework, we estimated the most likely sequence of hidden states in
+  each solute center-of-mass trajectory while simultaneously inferring VAR(1)
   parameters for each state and the overall state transition probability matrix, $T$.
   We created a python implementation of this process which we heavily adapted from
-  the MATLAB code of Fox et al.~\cite{fox_sticky_2007} Parameter estimation is iterative. 
+  %BJC: fox_bayesian is citation Emily Fox asked me to use.
+  the MATLAB code of Fox et al.~\cite{fox_bayesian_2010} Parameter estimation is iterative. 
   Therefore, we looked for convergence of each entry in the $\mathbf{c}$ vector as well
@@
   the time series of parameter estimates. Plots illustrating parameter convergence are 
-  available in Section~\ref{S-section:convergence} of the Supporting Information. We refer the interested reader to 
-  much more extensive descriptions of the inference and sampling procedures used to 
-  estimate the VAR(1) parameters and the state sequence. ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
-
+  available in Section~\ref{S-section:convergence} of the Supporting Information. We 
+  refer the interested reader to much more extensive descriptions of the inference and 
+  sampling procedures used to estimate the VAR(1) parameters and the state sequence. ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
+
+  %BJC: This paragraph could probably be cut down quite a bit. Leave justification for SI
   We carefully applied the IHMM algorithm in a way which takes advantage of the
-  system's cylindrical symmetry. There are a number of viable ways in which one 
-  could choose to analyze these time series. We could use all 3 dimensions straight
-  from the output trajectory. We could use just the $z$ dimensional coordinate 
-  since we are primarily interested in through-plane membrane transport. Ultimately, 
+  system's cylindrical symmetry. While there
+  %There 
+  are a number of viable ways in which one could choose to analyze these time series,
+  %BJC: cutting down on verbosity
+  % We could use all 3 dimensions straight
+  %from the output trajectory. We could use just the $z$ dimensional coordinate 
+  %since we are primarily interested in through-plane membrane transport. Ultimately, 
   we chose to use a multi-step procedure that we believe adequately distinguishes 
@@
   cylinder where we expect solutes to exhibit radially symmetric dynamics. We 
-  present a step-by-step demonstration of our procedure in Section~\ref{S-section:ihmm_procedure}
-  of the Supporting Information.
+  present a step-by-step demonstration of the procedure that follows in 
+  Section~\ref{S-section:ihmm_procedure} of the Supporting Information.
 
@@
   the Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. 
-  In Section~\ref{S-section:prior_guesses} of the Supporting Information we outline our method for 
-  choosing reliable prior parameters. The entries of $A$ and $\Sigma$ do 
-  not vary over a wide range, so the final parameters were relatively insensitive
-  to their priors.
+  In Section~\ref{S-section:prior_guesses} of the Supporting Information we 
+  outline our method for choosing reliable prior parameters. 
+%  The entries of $A$ and $\Sigma$ do 
+%  not vary over a wide range, so the final parameters were relatively insensitive
+%  to their priors.
 
@@
   state sequences. We evaluated the convergence of the state sequence based on
-  the convergence of the VAR parameters. The parameters of each states
+  the convergence of the VAR parameters. The parameters of each state
   generally converge within 500--1000 iterations. However, the boundaries of 
@@
   convergence (see Figure~\ref{S-fig:convergence3d} of the Supporting Information).
-
-  We defined the finalized parameters of each state as the average of the 
-  parameters from each iteration recorded after the equilibration time point.
-  We found the equilibration time point of each component of the $\mathbf{c}$ 
-  vector as well as $A$ and $\Sigma$ matrices, and then used the longest 
-  equilibration time of all dimensions as the equilibration time point.
-%  Further details are available in Section~\ref{S-section:convergence} of
-%  the Supporting Information.
 
@@
 
+  We defined the finalized parameters of each state as the average of the parameters 
+  from each iteration recorded after the equilibration time point. We found the 
+  equilibration time point of each component of the $\mathbf{c}$ vector as well as 
+  $A$ and $\Sigma$ matrices, and then used the longest equilibration time of all 
+  dimensions as the equilibration time point.
+
+  %BJC: I'll need to expand on this a bit to make it clear. Talk about the bootstrapping etc.
+  Finally, we generated stochastic trajectory realizations using the finalized
+  parameter sets. We drew state sequences with transition probabilities given by
+  $T$. While in a given state, we simulated motion according to the VAR(1)
+  parameterization of that state. After each state transition, we reset the 
+  unconditional mean of each state based on the particle's position immediately
+  before the state transition occurred.
+
+  \subsection{Parameter Clustering}\label{method:clustering}
+
   We clustered like parameter sets in order to reduce the state space to
@@
   similar clusters until a desired intracluster distance threshold or number of
-  clusters is reached.~\cite{pedregosa_scikit-learn_2011} We used the Ward linkage criteria, which works to minimize 
-  the sum of the squared differences within all clusters.~\cite{ward_hierarchical_1963}
-    %MRS6: explain why Ward (make the cluster as minimally disperse?)
-   	%BJC6: I'll add some plots to the SI and then write a better justification for
-	% the paper. This is lower priority in mind for the thesis.
-  We elected to choose the number of clusters rather than the distance threshold.
-  For our data, non-parametric methods such as Bayesian Gaussian mixture models~\cite{pedregosa_scikit-learn_2011,gelman_bayesian_2013} tend
-  to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
+  clusters is reached.~\cite{pedregosa_scikit-learn_2011} We used the Ward linkage 
+  criteria, which works to minimize the sum of the squared differences within all
+  clusters.~\cite{ward_hierarchical_1963} We elected to choose the number of clusters
+  rather than the distance threshold. For our data, non-parametric methods such as 
+  Bayesian Gaussian mixture models~\cite{pedregosa_scikit-learn_2011,gelman_bayesian_2013}
+  tend to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
   of the Supporting Information).
 
-  We clustered based on the two diagonal entries of $A$ and $\Sigma$ as well as the
-  radial means, $\mu_r$, for a total of 5 variables. One can choose alternative clustering
-  features, such as the eigenvalues of the $A$ and $\Sigma$ matrices, but we chose their 
-  diagonals because they can be easily translated to solute behavior. The diagonals of $A$
-  describe the correlation between sequential hops while the diagonals of $\Sigma$ describe
-  the size of the hops in each dimension. We assume that cross correlations in the parameters
-  are negligible for clustering.
-
-  We also chose to cluster the diagonals of each matrix and the radial means
-  independently before combining the clusters to assign final state labels. If we divide
-  the total states into $m$ clusters based on the diagonal entries of $A$, $n$ more clusters 
-  based on the diagonal entries of $\Sigma$, and $k$ clusters based on $\mu_r$, then there
-  are a total of $mnk$ possible cluster combinations. This allows slightly more flexibility
-  in the total number of states compared to clustering on all five features at once, since 
-  there can be up to, but not necessarily exactly, $mnk$ states.
-
+  We clustered based on the eigenvalues of $A$ and $\Sigma$, the radial means, $\mu_r$, 
+  and the self-transition probabilities, $T_{ii}$, of each state for a total of 6 clustering
+  dimensions. The means in $r$ are likely meaningful since the membrane is inhomogeneous, 
+  transitioning from hydrophilic pores to hydrophobic tails. To cluster on $T_{ii}$, we first
+  cast it in terms of the expected dwell times. The expected value of the number of sequential
+  self-transitions is simply $\frac{1}{1 - T_{ii}}$. This relationship correctly implies that 
+  dwell times approach infinity as $T_{ii}$ approaches 1. There we found the most success with
+  agglomerative clustering by linearizing this relationship and clustering on $-log(1 - T_{ii})$
+  (see Section\ref{S-section:selfT_cluster} of the Supporting Information for a graphical
+  illustration).
+
+%  One can choose alternative clustering
+%  features, such as the eigenvalues of the $A$ and $\Sigma$ matrices, but we chose their 
+%  diagonals because they can be easily translated to solute behavior. The diagonals of $A$
+%  describe the correlation between sequential hops while the diagonals of $\Sigma$ describe
+%  the size of the hops in each dimension. We assume that cross correlations in the parameters
+%  are negligible for clustering.
+%   
+%  We also chose to cluster the diagonals of each matrix and the radial means
+%  independently before combining the clusters to assign final state labels. If we divide
+%  the total states into $m$ clusters based on the diagonal entries of $A$, $n$ more clusters 
+%  based on the diagonal entries of $\Sigma$, and $k$ clusters based on $\mu_r$, then there
+%  are a total of $mnk$ possible cluster combinations. This allows slightly more flexibility
+%  in the total number of states compared to clustering on all five features at once, since 
+%  there can be up to, but not necessarily exactly, $mnk$ states.
+
+  %BJC: to be reworked after I have a working procedure.
   Choosing the number of clusters can be somewhat subjective so
@@
 
-  We remapped the state sequence based on the cluster assignments and generated a
-  state transition probability matrix, $T$. The IHMM algorithm also produces an estimate
-  of $T$, but since we fixed the state sequence, we decided to explicitly calculate $T$ 
-  by counting the number of transitions between states compiled across all trajectories.
-
-  We used the parameter inference component of the IHMM algorithm in order to 
-  infer $A$ and $\Sigma$ of the clustered states.
-   %BJC2: I'm unsure of the precise reasoning here.
-  We could not simply take the mean of the clustered $A$ and $\mathbf{e}_t$ 
-  parameters because it is not clear that this is a linear 
-  operation for this problem. To circumvent this problem, we modified the ($r$,
-  $z$) solute trajectories so that they had a mean of zero, leaving only the 
-  fluctuations. We did this by subtracting the mean from each same-state segment of the 
-  unclustered trajectory. We used the IHMM algorithm on this modified trajectory
-  to infer the clustered state parameters by fixing the clustered state sequence.
+  We remapped the state sequence based on the cluster assignments and parameterized
+  the clusters using the inference component of the IHMM algorithm. 
+%  generated a
+%  state transition probability matrix, $T$. The IHMM algorithm also produces an estimate
+%  of $T$, but since we fixed the state sequence, we decided to explicitly calculate $T$ 
+%  by counting the number of transitions between states compiled across all trajectories.
+%  We used the parameter inference component of the IHMM algorithm in order to 
+%  infer $A$ and $\Sigma$ of the clustered states.
+%  We could not simply take the mean of the clustered $A$ and $\mathbf{e}_t$ 
+%  parameters because it is not clear that this is a linear 
+%  operation for this problem. To circumvent this problem, 
+  First, we modified the ($r$, $z$) solute trajectories so that they had a mean of zero,
+  leaving only the fluctuations. We did this by subtracting the mean from each 
+  same-state segment of the unclustered trajectory. We used the IHMM algorithm on this
+  modified trajectory to infer the clustered state parameters by fixing the clustered 
+  state sequence.
 
@@
 
-  Finally, we generated stochastic trajectory realizations using the clustered
-  parameter sets. We drew state sequences with transition probabilities given by
-  $T$. While in a given state, we simulated motion according to the VAR(1)
-  parameterization of that state. After each state transition, we reset the 
-  unconditional mean of each state based on the particle's position immediately
-  before the state transition occurred.
+  %BJC:This next paragraph can probably be moved
+%  Finally, we generated stochastic trajectory realizations using the clustered
+%  parameter sets. We drew state sequences with transition probabilities given by
+%  $T$. While in a given state, we simulated motion according to the VAR(1)
+%  parameterization of that state. After each state transition, we reset the 
+%  unconditional mean of each state based on the particle's position immediately
+%  before the state transition occurred.
 
@@
   \section{Results and Discussion}
+
+  % BJC: It probably makes sense to put the trajectory generation and MSD predictions
+  % first since it will be part of how we justify our clustering choices.
 
@@
 
+%BJC: will move this earlier
   \subsection{Reproducing MD Trajectories and MSDs with the IHMM}

### 2020-05-07 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Filling in missing parts of draft

@@
 
+  \section{Parameter Convergence}\label{section:convergence}
+
+  The state sequence appears to converge within 500--1000 IHMM iterations. Step 1
+  in the procedure from the previous section is the only time the state sequence 
+  is determined. We ran 2000 iterations of the IHMM algorithm in order to arrive
+  at a finalized state sequence. Stabilization of the VAR parameters indicates 
+  that the state sequence has converged. In Figure~\ref{fig:convergence3d}, we plot
+  the diagonal entries of 3 different $A$ and $\Sigma$ matrices as well as the 
+  entries of the mean vector $\mathbf{c}$, fit to a single 3D methanol trajectory.
+  States with a relatively small number of observations are more highly influenced 
+  by the boundaries of the state segments and generally lead to much higher 
+  variance of the $A$ and $\Sigma$ parameters. In these cases, the mean is
+  a more reliable indicator of convergence since stabilized means imply that the
+  fluctuations assigned to each state come from motion about a static location.
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.8\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_47.pdf}
+  \caption{706 total emissions}\label{fig:convergence3d_MET_low}
+  \end{subfigure}
+  \begin{subfigure}{0.8\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_36.pdf}
+  \caption{1000 total emissions}\label{fig:convergence3d_MET_medium}
+  \end{subfigure}
+  \begin{subfigure}{0.8\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_59.pdf}
+  \caption{201 total emissions}\label{fig:convergence3d_MET_high}
+  \end{subfigure}
+  \caption{Given a sufficient number of observations for a given mode, the VAR parameters
+  appear to converge within 500 -- 1000 iterations. States with too few observations
+  are more highly influenced by the boundaries of the state segments and generally
+  lead to much higher fluctuations in the VAR parameters.}\label{fig:convergence3d}
+  \end{figure}
+
+  \clearpage
+
+  When we fix the state sequence in subsequent steps of the procedure, parameter 
+  estimates converge within only a few steps. In Figure~\ref{fig:fixed_state_convergence}, we 
+  plot the entries of $A$ and $\Sigma$ as a function of IHMM iteration. Some states
+  are sampled far more frequently than others. High sampling frequently results in
+  higher certainty converged parameter estimates. Due to fast convergence, we only
+  run 100 iterations of the inference behavior when the state sequence is fixed.
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.6\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_4.pdf}
+  \caption{15 total emissions}\label{fig:convergence_MET_low}
+  \end{subfigure}
+  \begin{subfigure}{0.6\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_21.pdf}
+  \caption{1289 total emissions}\label{fig:convergence_MET_medium}
+  \end{subfigure}
+  \begin{subfigure}{0.6\textwidth}
+  \includegraphics[width=\textwidth]{convergence_MET_15.pdf}
+  \caption{24468 total emissions}\label{fig:convergence_MET_high}
+  \end{subfigure}
+  \caption{The VAR parameters converge quickly when we fix the state
+  sequence. As the total number of emissions observed from each state
+  increases, the uncertainty in the converged parameters estimates
+  decreases.}\label{fig:fixed_state_convergence}
+  \end{figure}
+
+  \clearpage
+
   \section{Demonstration of IHMM Parameterization Procedure}\label{section:ihmm_procedure}
 
-  Parameterization of trajectories by the IHMM is a multi-stepped procedure. In the figures
-  that follow, we graphically illustrate the procedure which is described in detail in
-  Section~\ref{M-method:IHMM} of the main text.
+  Parameterization of trajectories by the IHMM is a multi-stepped procedure. In the steps and
+  figures that follow, we graphically illustrate the procedure which is described in detail 
+  in Section~\ref{M-method:IHMM} of the main text.
 
@@
   	pore center (see Figure~\ref{fig:xyz_hmm}). 	
-  	\item Convert $x$ and y coordinates to radial coordinates, $r$, then fix the state sequence
+  	\item Convert $x$ and $y$ coordinates to radial coordinates, $r$, then fix the state sequence
   	and use the inference component of the IHMM in order to estimate the parameters in terms
@@
 
-  \section{Parameter Convergence}\label{section:convergence}
+  \section{Clustering}\label{section:clustering}
 
-  The state sequence appears to converge within 500--1000 IHMM iterations. Step 1
-  in the procedure from the previous section is the only time the state sequence 
-  is determined. We ran 2000 iterations of the IHMM algorithm in order to arrive
-  at a finalized state sequence. Stabilization of the VAR parameters indicates 
-  that the state sequence has converged. In Figure~\ref{fig:convergence3d}, we plot
-  the diagonal entries of 3 different $A$ and $\Sigma$ matrices as well as the 
-  entries of the mean vector $\mathbf{c}$, fit to a single 3D methanol trajectory.
-  States with a relatively small number of observations are more highly influenced 
-  by the boundaries of the state segments and generally lead to much higher 
-  variance of the $A$ and $\Sigma$ parameters. In these cases, the mean is
-  a more reliable indicator of convergence since stabilized means imply that the
-  fluctuations assigned to each state come from motion about a static location.
-
-  \begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.8\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_47.pdf}
-  \caption{706 total emissions}\label{fig:convergence3d_MET_low}
-  \end{subfigure}
-  \begin{subfigure}{0.8\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_36.pdf}
-  \caption{1000 total emissions}\label{fig:convergence3d_MET_medium}
-  \end{subfigure}
-  \begin{subfigure}{0.8\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_59.pdf}
-  \caption{201 total emissions}\label{fig:convergence3d_MET_high}
-  \end{subfigure}
-  \caption{Given a sufficient number of observations for a given mode, the VAR parameters
-  appear to converge within 500 -- 1000 iterations. States with too few observations
-  are more highly influenced by the boundaries of the state segments and generally
-  lead to much higher fluctuations in the VAR parameters.}\label{fig:convergence3d}
-  \end{figure}
-
-  \clearpage
-
-  When we fix the state sequence in subsequent steps of the procedure, parameter 
-  estimates converge within only a few steps. In Figure~\ref{fig:fixed_state_convergence}, we 
-  plot the entries of $A$ and $\Sigma$ as a function of IHMM iteration. Some states
-  are sampled far more frequently than others. High sampling frequently results in
-  higher certainty converged parameter estimates. Due to fast convergence, we only
-  run 100 iterations of the inference behavior when the state sequence is fixed.
-
-  \begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.6\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_4.pdf}
-  \caption{15 total emissions}\label{fig:convergence_MET_low}
-  \end{subfigure}
-  \begin{subfigure}{0.6\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_21.pdf}
-  \caption{1289 total emissions}\label{fig:convergence_MET_medium}
-  \end{subfigure}
-  \begin{subfigure}{0.6\textwidth}
-  \includegraphics[width=\textwidth]{convergence_MET_15.pdf}
-  \caption{24468 total emissions}\label{fig:convergence_MET_high}
-  \end{subfigure}
-  \caption{The VAR parameters converge quickly when we fix the state
-  sequence. As the total number of emissions observed from each state
-  increases, the uncertainty in the converged parameters estimates
-  decreases.}\label{fig:fixed_state_convergence}
-  \end{figure}
-
-  \clearpage
-
-  \section{Agglomerative Clustering Versus Gaussian Mixture Models}\label{section:agglomerative}
+  \subsection{Agglomerative Clustering Versus Gaussian Mixture Models}\label{section:agglomerative}
 
@@
 
-  \section{Choosing the Number of Clusters}\label{section:nclusters}
+  \subsection{Clustering on the self-transition probabilities}\label{section:selfT_cluster}
+
+  To cluster on $T_{ii}$, we first
+  cast it in terms of the expected dwell times. The expected value of the number of sequential
+  self-transitions is simply $\frac{1}{1 - T_{ii}}$. This relationship correctly implies that 
+  dwell times approach infinity as $T_{ii}$ approaches 1. There we found the most success with
+  agglomerative clustering by linearizing this relationship and clustering on $-log(1 - T_{ii})$.
+
+  \subsection{Choosing the Number of Clusters}\label{section:nclusters}
 

### 2020-05-07 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
Filling in missing parts of draft

@@
   H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
-  predict solute mean squared displacements (MSDs) and solute flux, and thus 
-  solute selectivity, in macroscopic length pores.
+  predict solute mean squared displacements (MSDs), solute flux, and
+  solute selectivity in macroscopic length pores.
 
@@
 
-  Highly selective separations membranes are desirable in numerous
+  Highly selective separation membranes are desirable in numerous
   applications. The ability to efficiently separate ions from saline water
@@
   an ideal geometry for high throughput separations.~\cite{feng_scalable_2014,feng_thin_2016}
-  %BJCB: could add a sentence saying that in pracftice, alignment is hard. Not sure if worth acknowledging for this paper.
-  %MRSB: nah, not here.
 
@@
   dynamics (MD) simulations to study the transport of 20 small polar molecules
-  in an H\textsubscript{II} phase LLC membrane. We chose to study the
-  H\textsubscript{II} phase because it is a simpler geometry to model than the
-  Q\textsubscript{I} phase and significantly more structural data is available
-  to help ensure molecular models are consistent with experiment. In general,
+  in an H\textsubscript{II} phase LLC membrane. 
+  %We chose to study the
+  %H\textsubscript{II} phase because it is a simpler geometry to model than the
+  %Q\textsubscript{I} phase and significantly more structural data is available
+  %to help ensure molecular models are consistent with experiment. 
+  In general,
   we observed subdiffusive transport behavior characterized by intermittent
@@
 
-  We fit sFBM models in two ways: First, we parameterize solute motion using
-  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
-  Second, we use a two-state approach by extracting two sets of model parameters
-  calculated based on a solute's radial distance from the closest pore center. 
-  This allows us to include the different dynamical behavior of solutes previously
-  observed within the pore region versus within the monomer tails.
+% BJCC: I cut this, doesn't really seem to be necessary for intro
+%  We fit sFBM models in two ways: First, we parameterize solute motion using
+%  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
+%  Second, we use a two-state approach by extracting two sets of model parameters
+%  calculated based on a solute's radial distance from the closest pore center. 
+%  This allows us to include the different dynamical behavior of solutes previously
+%  observed within the pore region versus within the monomer tails.
 
@@
   third of the water molecules occupy the tail region with the rest near the
-  pore center. We chose to focus our study on the 10 wt\% water system because
-  solutes move significantly faster than in the 5 wt\% system studied
-  previously, thus allowing more statistically valid analyses.
+  pore center.
+%BJCC: I don't see a need to justify 10 over 5 wt% 
+%  We chose to focus our study on the 10 wt\% water system because
+%  solutes move significantly faster than in the 5 wt\% system studied
+%  previously, thus allowing more statistically valid analyses.
 
@@
   motion and when $H > 0.5$, one observes positive correlation between hops. 
-
-  There are many methods for estimating the Hurst parameter for a time series.
-  \cite{clegg_practical_2006} It can be a difficult task because 
-  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
-  $H > 0.5$, meaning one needs to study large time lags with high frequency.
-  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
-  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
-  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
-  fitting longer time lags to our data is lost in the noise since the analytical values
-  are so close to zero. Therefore, we obtained $H$ by performing a least squares fit of 
-  Equation~\ref{eqn:fbm_autocorrelation} to the first 
-  ten 0.5 ns time lags of the empirically measured autocorrelation function.
+  We obtained $H$ by performing a least squares fit of 
+  Equation~\ref{eqn:fbm_autocorrelation} to the first ten 0.5 ns time lags of 
+  the empirically measured autocorrelation function (see section~\ref{S-section:H_estimate}
+  of the Supporting Information for a more in depth justification of this method).
+
+% BJCC: left this discussion for supporting. Added last sentence above
+%  There are many methods for estimating the Hurst parameter for a time series.
+%  \cite{clegg_practical_2006} It can be a difficult task because 
+%  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
+%  $H > 0.5$, meaning one needs to study large time lags with high frequency.
+%  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
+%  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
+%  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
+%  fitting longer time lags to our data is lost in the noise since the analytical values
+%  are so close to zero. Therefore, we obtained $H$ by performing a least squares fit of 
+%  Equation~\ref{eqn:fbm_autocorrelation} to the first 
+%  ten 0.5 ns time lags of the empirically measured autocorrelation function.
 
@@
   under-sample the tails. We chose to truncate the L\'evy stable distributions
-  based on where the theoretical probability distribution function (PDF) starts
+  based on where the theoretical PDF starts
   to deviate from the empirically measured PDF (see
@@
 	  \hline
-	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
+	  Dwell Distribution                & ~~~~~~Hop Length Distribution~~~~~~ & Abbreviation \\
 	  \hline
@@
   distribution of dwell times are both characteristic of CTRWs
-  (See Figures~\ref{S-fig:hop_distribution_comparison} and~\ref{S-fig:powerlaw}
-  of the Supporting Information). 
+  (See Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). 
   %The apparent
@@
   structures of hop lengths are close to those observed in our simulations 
-  (See Figure~\ref{S-fig:hop_acf} of the Supporting Information). Fractional 
+  (See Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). Fractional 
   motion is common in crowded viscoelastic environments where motion is highly
@@
   to L\'evy stable distributions since it is more general than the Gaussian
-  distribution. We plotted the MLE fits of both on top of urea's hop length
-  distribution in Figure~\ref{S-fig:hop_distribution_comparison} of the
+  distribution. We plotted the MLE fits of both on top of each solute's hop length
+  distribution in Figure~\ref{S-fig:anticorrelated_hops} of the
   Supporting Information. The L\'evy distribution does a better job capturing
-  the somewhat heavy tails and high density near 0 of the hop length distribution. 
+  the somewhat heavy tails and high density near 0 of the hop length distributions. 
   However, since there are no known exact simulation techniques for generating 
@@
   worthwhile. In fact, we typically observe very little difference between model
-  predictions parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).
+  predictions parameterized with FLM versus FBM.% (see Figure~\ref{fig:anomalous_msds}).
 
@@
   On long time scales, the density of the truncated power law drops below that
-  of the pure power law and tends towards 0 near a dwell time of 250 ns.
+  of the pure power law and tends towards 0. % near a dwell time of 250 ns.
 
@@
   ns, may not exist in the MD system. Eventual loss of correlation would result 
-  in a shift from sub-linear to linear MSD behavior, as observed in the MD 
+  in a shift from sub-linear, or subdiffusive, to linear, or diffusive, MSD behavior, as observed in the MD 
   trajectories. Acetic acid exemplifies this point. At first glance, acetic acid's
@@
   region. Tail region hydrogen bonds are donated from methanol to the ether
-  linkages between the monomer head groups and tails. One might modify the
+  linkages between the monomer head groups and tails, as well as to the ester groups
+  at the ends of the tails. One might modify the
   rate of methanol transport by controlling its partition into the monomer
@@
 	  solute flux versus pore length, $L$, to a power law function of the
-	  form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
+	  form $AL^{-\beta}$ (dashed lines). 
   }\label{fig:flux_curves}
@@
   sense since higher degrees of anti-correlation should slow the rate at which
-  solutes cross the membrane pore. When we remove anti-correlation between
+  solutes cross a membrane pore of a given length. When we remove anti-correlation between
   hops (set $H$=0.5), the length dependence becomes the same for all solutes,

### 2020-05-07 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Filling in missing parts of draft

@@
   \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
-  \texttt{/analysis/ Markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
+  \texttt{/analysis/ markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
   \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD approach. \\\hline 
@@
 
-  In Figure~\ref{fig:hurst_autocorrelation}, we plotted Equation~\ref{eqn:fbm_autocorrelation}
-  for different values of $H$. When $H > 0.5$, Equation~\ref{eqn:fbm_autocorrelation} decays
-  slowly to zero meaning one needs to study large time lags with high frequency in order to
-  accurately estimate $H$ from the data. Fortunately, all of our solutes show anti-correlated
-  motion, so most of the information in Equation \ref{eqn:fbm_autocorrelation} is contained
-  within the first few lags.
+  There are many methods for estimating the Hurst parameter for a time series.
+  \cite{clegg_practical_2006} It can be a difficult task because 
+  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
+  $H > 0.5$, meaning one needs to study large time lags with high frequency.
+
+  Fortunately, from a mathematical perspective, all of our solutes show anti-correlated
+  motion, so most of the information in Equation~\ref{eqn:fbm_autocorrelation} is contained
+  within the first few time lags. In Figure~\ref{fig:hurst_autocorrelation}, we plotted
+  Equation~\ref{eqn:fbm_autocorrelation} for different values of $H$. When $H > 0.5$, 
+  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero meaning one needs to study
+  large time lags with high frequency in order to accurately estimate $H$ from the data. 
+  However, when $H < 0.5$, the autocorrelation function quickly decays towards zero.
 
@@
   distribution near the mean, but under-samples the tails. In 
-  Figure~\ref{fig:truncation_correction} we compare the empirically 
+  Figure~\ref{fig:truncation_cutoff} we compare the empirically 
   measured transition emission distribution of the MSDDM for urea to its maximum likelihood fit to
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{truncation_correction.pdf}
-  \caption{We can accurately truncate the marginal distribution of FLM innovations by
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{truncation_correction.pdf}
+  \caption{}\label{fig:truncation_correction}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{hurst_correction.pdf}
+  \caption{}\label{fig:hurst_correction}
+  \end{subfigure}
+  \caption{(a) We can accurately truncate the marginal distribution of FLM innovations by
   applying a correction to the input truncation parameter. We generated FLM sequences
@@
   parameter with our database resulting in a distribution close to the theoretical
-  distribution (black dashed line) with a maximum value close to 0.5.}\label{fig:truncation_correction}
+  distribution (black dashed line) with a maximum value close to 0.5.
+  (b) Correcting the Hurst parameter input to the algorithm of Stoev and Taqqu
+  results in an FLM process with a more accurate correlation structure. We generated
+  sequences with an input $H$ of 0.35. We estimated $H$ by fitting the autocorrelation
+  function. Without the correction, $H$ is underestimated, meaning realizations are 
+  more negatively correlated than they should be. }
   \end{figure}
@@
 
-  % /supporting_figures/demonstrate_hurst_correction.py
-  \begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{hurst_correction.pdf}
-  \caption{Correcting the Hurst parameter input to the algorithm of Stoev and Taqqu
-  results in an FLM process with a more accurate correlation structure. We generated
-  sequences with an input $H$ of 0.35. We estimated $H$ by fitting the autocorrelation
-  function. Without the correction, $H$ is underestimated, meaning realizations are 
-  more negatively correlated than they should be.}\label{fig:hurst_correction}
-  \end{figure}
+%  % /supporting_figures/demonstrate_hurst_correction.py
+%  \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{hurst_correction.pdf}
+%  \caption{Correcting the Hurst parameter input to the algorithm of Stoev and Taqqu
+%  results in an FLM process with a more accurate correlation structure. We generated
+%  sequences with an input $H$ of 0.35. We estimated $H$ by fitting the autocorrelation
+%  function. Without the correction, $H$ is underestimated, meaning realizations are 
+%  more negatively correlated than they should be.}\label{fig:hurst_correction}
+%  \end{figure}
 
@@
   same kind of anti-correlated hopping and trapping behavior.
-
-  \begin{figure}[h]
+%  
+  \begin{figure}[htb!]
   \centering
@@
   \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
-  \caption{}\label{fig:hop_distribution_comparison}
+  \caption{}\label{fig:URE_hop_distribution_comparison}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
-  \caption{}\label{fig:powerlaw}
+  \caption{}\label{fig:URE_powerlaw}
   \end{subfigure}
@@
   \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
-  \caption{}\label{fig:hop_acf}
+  \caption{}\label{fig:URE_hop_acf}
   \end{subfigure}
@@
   respectively for urea (a-c), ethylene glycol (d-f), acetic acid (g-i), and methanol (j-l).
-  Using urea as an example, (a) the distribution of hop lengths can be fit by a Gaussian in
-  addition to a more general L\'evy stable distribution, though the L\'evy stable distribution
-  does a better job of capturing the heavier tails and increased density near 0. We explore
-  models fit to both distributions, as Gaussian hops are more convenient to model. (b) The 
-  distribution of dwell times is fit well by a power law but it over-estimates the probability
-  density at long dwell times. A power law truncated with an exponential cut-off better
-  describes the probability of long dwell times in our simulations. (c) The hops are negatively
-  correlated to their previous hop. In combination, (a) -- (c) support modeling solutes as either
-  subordinated fractional Brownian or L\'evy motion.
+%  Using urea as an example, (a) the distribution of hop lengths can be fit by a Gaussian in
+%  addition to a more general L\'evy stable distribution, though the L\'evy stable distribution
+%  does a better job of capturing the heavier tails and increased density near 0. We explore
+%  models fit to both distributions, as Gaussian hops are more convenient to model. (b) The 
+%  distribution of dwell times is fit well by a power law but it over-estimates the probability
+%  density at long dwell times. A power law truncated with an exponential cut-off better
+%  describes the probability of long dwell times in our simulations. (c) The hops are negatively
+%  correlated to their previous hop. In combination, (a) -- (c) support modeling solutes as either
+%  subordinated fractional Brownian or L\'evy motion.
   }\label{fig:anticorrelated_hops}
@@
 	  correlated to each other. The normalized version of
-	  Equation~\ref{M-eqn:flm_autocovariance} fits well to the data
+	  Equation~\ref{M-eqn:flm_autocovariance} of the main text fits well to the data
 	  suggesting FLM is an appropriate way to model jumps.}

### 2020-05-07 Ben_Manuscripts/stochastic_transport/arxiv/ms.tex
Filling in missing parts of draft

--- 2020-04-16 Ben_Manuscripts/stochastic_transport/arxiv/ms.tex
@@
 \usepackage{float}
-\usepackage{xr}
 \usepackage{diagbox}
@@
 
+\SectionNumbersOn
+
+\usepackage[utf8]{inputenc}
 \DeclareUnicodeCharacter{03C9}{$\omega$}
@@
 
-  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
-  with Time Series Modeling}
-
-  \author{Benjamin J. Coscia}
-  \author{Michael R. Shirts}
-
-  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}
-
-  \date{\today}
-
   \begin{abstract}
 
-  Mathematically modeling complex transport phenomena at the molecular level 
-  can be a powerful tool for identifying transport mechanisms and predicting
-  macroscopic properties. We use two different stochastic time series models,
-  parameterized from long molecular dynamics (MD) simulation trajectories of
-  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
-  membrane, in order to predict solute mean squared displacements (MSDs) 
-  and solute flux, and thus solute selectivity, in macroscopic length pores.
+  Mathematically modeling complex transport phenomena can be a powerful tool
+  for extracting important physical information from molecular simulations. 
+  In this study, we present two new approaches that use stochastic time series
+  modeling to predict long time-scale behavior and macroscopic properties 
+  from molecular simulation which can be generalized to other molecular systems
+  where complex diffusion occurs. Specifically, we parameterize our models using
+  long molecular dynamics (MD) simulation trajectories of a cross-linked 
+  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
+  predict solute mean squared displacements (MSDs), solute flux, and
+  solute selectivity in macroscopic length pores.
 
@@
   dwell times, hop lengths between dwells and correlation between hops. We 
-  explore two variations of the anomalous diffusion modeling approach. The first variation
-  applies a single set of parameters to the solute displacements and the second
-  applies two sets of parameters based on the solute's radial distance from the
-  closest pore center.
-
-  Next, we generalize Markov state models, treating the
-  configurational states of the system as a Markov process where each
-  state has distinct transport properties. For each state and transition
-  between states, we parameterize the distribution and temporal correlation 
-  structure of positional fluctuations as a means of characterization and to 
-  allow us to predict solute MSDs. We show that both models reasonably reproduce
-  the MSDs calculated from MD simulations. However, qualitative differences 
-  between MD and Markov state dependent model-generated trajectories may limit 
-  its usefulness.
-
-  Finally, we demonstrate how one can use these models to 
-  estimate flux of a solute across a macroscopic-length pore and, based on 
-  those quantities, the membrane's selectivity towards each solute. This work 
-  helps to connect microscopic chemically-dependent solute motions that do not
-  follow simple diffusive behavior with macroscopic membrane performance.
+  explore two variations of the anomalous diffusion modeling approach. The first 
+  variation applies a single set of parameters to the solute displacements and 
+  the second applies two sets of parameters based on the solute's radial distance
+  from the closest pore center.
+
+  Next, we present an approach that generalizes Markov state models, treating 
+  the configurational states of the system as a Markov process where each 
+  state has distinct transport properties. For each state and transition between
+  states, we parameterize the distribution and temporal correlation structure of
+  positional fluctuations as a means of characterization and to allow us to
+  predict solute MSDs.
+
+  We show that both stochastic models reasonably reproduce the MSDs calculated 
+  from MD simulations. However, qualitative differences between MD and Markov 
+  state dependent model-generated trajectories may in some cases limit their 
+  usefulness. With these parameterized stochastic models, we demonstrate how 
+  one can estimate flux of a solute across a macroscopic-length pore and, based
+  on those quantities, the membrane's selectivity towards each solute. This
+  work therefore helps to connect microscopic, chemically-dependent solute 
+  motions that do not follow simple diffusive behavior with long time-scale 
+  behavior, in an approach generalizable to many types of molecular systems 
+  with complex dynamics.
 
@@
 
-  Highly selective separations membranes are desirable in numerous
+  There is a large disparity between the time scales accessible to atomistic 
+  molecular dynamics (MD) simulations and experiment. The dynamics of molecules 
+  over nanoseconds of simulation may tell a very different story than that 
+  inferred by bulk measurements on the time-scale of seconds. Understanding 
+  complex dynamical behavior on short time-scales and connecting them with much
+  longer time-scales can provide fundamental insight which can be used for 
+  atomic level design of materials. In this work, we pursue this connection 
+  applied to highly selective aqueous filtration membranes and demonstrate how
+  one can gain chemical intuition which serves both theoretical and experimental
+  researchers.
+
+  Highly selective separation membranes are desirable in numerous
   applications. The ability to efficiently separate ions from saline water
@@
   potentially harmful organic micropollutants such as fertilizers, pesticides,
-  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} In
-  the materials industry, there is a strong interest in creating breathable
-  fabrics which selectively allow passage of water
-  vapor.~\cite{mondloch_destruction_2015}
-
+  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} 
+  %BJCB: could cut this last sentence. It's kind of awkward  
+  %MRSB: agree  
+  %In the materials industry, there is a strong interest in creating breathable
+  %fabrics which selectively allow passage of water
+  %vapor.~\cite{mondloch_destruction_2015}
+
+  % BJCA: I could likely condense this paragraph to focus primarily on the HII phase
+  % and its complex pores.
+  %MRS: yes.  QI not relevant
+%  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
+%  can be cross-linked into mechanically strong and highly selective nanoporous
+%  membranes.~\cite{gin_polymerized_2008} They may provide a promising
+%  alternative to conventional membrane separation techniques by being selective
+%  based not only on solute size and charge, but on solute chemical
+%  functionality as well.~\cite{dischinger_application_2017} One can tune the
+%  functionality of LLC monomers in order to enhance or weaken specific
+%  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
+%  morphologies of LLC membranes are being actively developed. The inverted
+%  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
+%  pores on the order of 1 nm in size. A perfectly synthesized
+%  H\textsubscript{II} phase has an ideal geometry for high throughput
+%  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
+%  a large scale as required for high permeability has shown limited
+%  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
+%  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
+%  complex pores of the H\textsubscript{II} phase but its geometry consists of a
+%  tortuous network of 3D interconnected pores which do not require
+%  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
+%  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
+%  H\textsubscript{II} phase, it is considerably easier to produce 
+%  at scale.~\cite{hatakeyama_nanoporous_2010}
+
+  %BJCB: removed discussion of Q1 from above paragraph
   Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
@@
   functionality of LLC monomers in order to enhance or weaken specific
-  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
-  morphologies of LLC membranes are being actively developed. The inverted
-  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
-  pores on the order of 1 nm in size. A perfectly synthesized
-  H\textsubscript{II} phase has an ideal geometry for high throughput
-  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
-  a large scale as required for high permeability has shown limited
-  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
-  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
-  complex pores of the H\textsubscript{II} phase but its geometry consists of a
-  tortuous network of 3D interconnected pores which do not require
-  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
-  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
-  H\textsubscript{II} phase, it is considerably easier to produce 
-  at scale.~\cite{hatakeyama_nanoporous_2010}
-
-  Molecular modeling may make it possible to efficiently evaluate
-  solute-specific separation membranes using the available chemical space of
-  LLC monomers. To date, only a limited subset of LLC monomers have been
-  studied experimentally in membrane applications.
-  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
+  solute-membrane interactions.~\cite{dischinger_effect_2017}
+
+  % BJCB: split into two paragraphs  
+  In this work, we study the inverted hexagonal, H\textsubscript{II}, LLC phase. 
+  The H\textsubscript{II} phase has densely packed, uniform-sized pores on the 
+  order of 1 nm in size. A perfectly aligned H\textsubscript{II} phase has 
+  an ideal geometry for high throughput separations.~\cite{feng_scalable_2014,feng_thin_2016}
+
+  Molecular modeling may make it possible to efficiently evaluate solute-specific
+  separation membranes using the available chemical space of LLC monomers by 
+  allowing researchers to understand their macroscopic behavior based on 
+  microscopic, chemically-dependent solute motions. To date, only a limited 
+  subset of H\textsubscript{II} phase-forming LLC monomers have been studied
+  experimentally in membrane applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
   Even within this small subset, they have demonstrated selectivities that
@@
   trajectories per unit cell in order to minimize solute-solute interactions.
-% BJC2: removed this sentence. High uncertainty MSDs don't really relate to long timescale predictions. Unless the MSDs were linear.
-%  This results in relatively high uncertainties in observables such as mean
-%  squared displacement (MSD), preventing reliable long timescale predictions.
   We are in need of an efficient method which can use our limited atomistic 
   simulation data sets in order to predict long timescale solute behavior.
-  %BJC2: following sentence replaced with above
-%  We are in need of a way of studying the collective motion of a much larger
-%  set of solutes over much longer timescales.
-  %MRS11: Maybe this last sentence could be changed. Because you aren't really finding a way to study larger sets of 
-  %solutes over larger timescales, you are using a limited amount of atomistic simulation into long time scale behavior efficiently. We can discuss variations as needed!
-
-  %BJC: maybe this paragraph can be cut down?
+
   Mathematical descriptions of transport in complex separations membranes are a
@@
   making long timescale predictions with computational ease and lower
-  uncertainties. Fortunately, there is an abundance of information encoded in
+  uncertainties. There is an abundance of information encoded in
   the complex solute trajectories. One can incorporate fluctuations and 
@@
   their inputs are parameterized using a substantial amount of data generated
-  by long ($\geq 5~\mu$s) MD simulations.
-
-  % BJC: I'd say this is where the intro starts to get technical
-%  We constructed our first model by applying the existing rigorous theoretical
-%  foundation which describes the motion of particles that exhibit non-Brownian,
-%  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
-%  introduced by fractional calculus are instrumental to this
-%  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
-%  normally linear diffusion equation to fractional derivative orders, providing
-%  descriptions of a much more diverse set of behavior, including subdiffusion,
-%  a type of anomalous diffusion exhibited by solutes in this
-%  study.~\cite{klages_anomalous_2008}
-
-  %MRS11: should be clear if first model is previous publications, or what is presented here.
-  %If what is presented here, should talk about how it will be presented, not that it was developed. 
-  %MRS11: research activities happened in the past, presentation of research is described in the present.
-  %or potentially future if describing what will be presented in the rest of the paper. 
-  %BJC: replacement to above.
-  %BJC1: Made clear that this is talking about the first model of this work.
-  %BJC1: went through rest of intro to make sure tense is consistent
-  The first model that we develop in this work allows us to characterize the 
-  hopping and trapping behavior displayed by solutes in our MD simulations. This 
-  type of non-Brownian dynamical behavior results in subdiffusive transport which
-  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
-  %MRS12: removing paragraph break
-  % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
-  % stole thesis from paragraph below it
+  by long ($\geq 5~\mu$s) MD simulations. Where sufficiently close to observed data,
+  these fitted models provide a way to propagate information about solute 
+  trajectories gathered at the microsecond time scale to realistic experimental 
+  time scales.
+
+  We constructed our first model by applying the existing rigorous theoretical
+  foundation which describes the motion of particles that exhibit non-Brownian,
+  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} 
+  The tools introduced by fractional calculus are instrumental to this 
+  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the normally
+  linear diffusion equation to fractional derivative orders, providing descriptions
+  of a much more diverse set of behavior, including subdiffusion, a type of 
+  anomalous diffusion exhibited by solutes on the simulation time scales of this
+  study.~\cite{klages_anomalous_2008}
+
   We treat our system in terms of two well-known classes of anomalous
@@
 
-%  Three well-known classes of behavior leading to anomalous subdiffusion are
-%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
-%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
-%  motion are frequently used alone or in combination to describe single
-%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
-%  is characterized by a distribution of hop lengths and dwell times, where
-%  trajectories consist of sequential independent random draws from each
-%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
-%  viscoelastic environments where each jump comes from a Gaussian distribution
-%  but is anti-correlated to its previous
-%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
-%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
-%  dead ends cause anti-correlated
-%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
-
-%  We treated our system as an FBM process subordinate to a CTRW, or
-%  subordinated FBM (sFBM) for short. 
-  We fit sFBM models in two ways: First, we parameterize solute motion using
-  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
-  Second, we use a two-state approach by extracting two sets of model parameters
-  calculated based on a solute's radial distance from the closest pore center. 
-  This allows us to include the different dynamical behavior of solutes previously
-  observed within the pore region versus within the monomer tails.
-
-  Where sufficiently close to observed data, these fitted sFBM models
-  provide a way to propagate information about solute trajectories gathered 
-  at the microsecond time scale to realistic experimental time scales. 
-  They can also confirm the importance of assumed solute-membrane interactions 
-  used to define the model's functional form, and
-  suggest missing components. They can help researchers formulate hypotheses to
-  explain why a certain set of parameters is characteristic to a specific
-  solute.
+% BJCC: I cut this, doesn't really seem to be necessary for intro
+%  We fit sFBM models in two ways: First, we parameterize solute motion using
+%  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
+%  Second, we use a two-state approach by extracting two sets of model parameters
+%  calculated based on a solute's radial distance from the closest pore center. 
+%  This allows us to include the different dynamical behavior of solutes previously
+%  observed within the pore region versus within the monomer tails.
 
@@
 
-  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
-  anomalous diffusion. During an anomalous diffusion process, the mean squared 
-  displacement (MSD) does not grow linearly with time, but instead it follows 
-  a power law of the form: 
+  On the time scales simulated in this study, solutes in this system very 
+  clearly exhibit subdiffusive behavior, a type of anomalous diffusion. 
+  During an anomalous diffusion process, the mean squared displacement (MSD)
+  does not grow linearly with time, but instead it follows a power law of 
+  the form: 
   \begin{equation} 
@@
   we do not simulate enough independent solute trajectories to obtain a reliable
-  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
-  time distributions described in subsequent sections.
-
+  estimate. It is also possible that solute dynamics will become diffusive on
+  long simulation timescales. Therefore, the transition from subdiffusion to regular
+  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD
+  curves. We can obtain higher precision estimates of $\alpha$ using the dwell
+  time distributions as described in subsequent sections.
+
+  % BJCB: condensed commented out section that follows into this paragraph
   In this study, we primarily use the MSD as a tool for characterizing the average
-  dynamic behavior of solute trajectories. Rather than using them to calculate 
-  diffusion constants or to relate our simulations to experimental measurements, we
-  compare MSDs calculated from MD simulations to those generated from our models 
-  in order to validate those models. Therefore, it is only important that we use a
+  dynamic behavior of solute trajectories. Therefore, it is only important that we use a
   consistent definition for calculating the MSD between modeled trajectories and
-  directly observed MD trajectories.
-
-  One can measure MSD in two ways. The ensemble averaged MSD measures 
-  displacements with respect to a particle's initial position:
-  \begin{equation}
-  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
-  \label{eqn:ensemble_msd}
-  \end{equation}
-  Fits to the ensemble averaged MSD will always reproduce the form of 
-  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
-  displacements over time lag $\tau$: 
+  directly observed MD trajectories. We chose to calculate the time-averaged MSD from 
+  our MD simulations and stochastic models which measures all observed displacements
+  over time lag $\tau$: 
   \begin{equation}
@@
   likelihood function:~\cite{clauset_power-law_2009}
+%  \begin{equation}
+%    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
+%  \label{eqn:powerlaw_cutoff_likelihood}
+%  \end{equation}
   \begin{equation}
@@
   motion and when $H > 0.5$, one observes positive correlation between hops. 
-
-  There are many methods for estimating the Hurst parameter for a time series.
-  \cite{clegg_practical_2006} It can be a difficult task because 
-  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
-  $H > 0.5$, meaning one needs to study large time lags with high frequency.
-  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
-  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
-  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
-  fitting longer time lags to our data is lost in the noise since the analytical values
-  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
-  Equation~\ref{eqn:fbm_autocorrelation} to the first 
-  ten 0.5 ns time lags of the empirically measured autocorrelation function.
+  We obtained $H$ by performing a least squares fit of 
+  Equation~\ref{eqn:fbm_autocorrelation} to the first ten 0.5 ns time lags of 
+  the empirically measured autocorrelation function (see section~\ref{S-section:H_estimate}
+  of the Supporting Information for a more in depth justification of this method).
+
+% BJCC: left this discussion for supporting. Added last sentence above
+%  There are many methods for estimating the Hurst parameter for a time series.
+%  \cite{clegg_practical_2006} It can be a difficult task because 
+%  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
+%  $H > 0.5$, meaning one needs to study large time lags with high frequency.
+%  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
+%  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
+%  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
+%  fitting longer time lags to our data is lost in the noise since the analytical values
+%  are so close to zero. Therefore, we obtained $H$ by performing a least squares fit of 
+%  Equation~\ref{eqn:fbm_autocorrelation} to the first 
+%  ten 0.5 ns time lags of the empirically measured autocorrelation function.
 
@@
   Fourier transform of a L\'evy stable PDF is: 
+%  \begin{equation}
+%    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
+%  \end{equation}
   \begin{equation}
@@
   FLM is:
+%  \begin{equation}
+%    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
+%    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
+%    \label{eqn:flm_autocovariance}
+%  \end{equation}
   \begin{equation}
@@
   under-sample the tails. We chose to truncate the L\'evy stable distributions
-  based on where the theoretical probability distribution function (PDF) starts
+  based on where the theoretical PDF starts
   to deviate from the empirically measured PDF (see
-  Section~\ref{S-section:truncation} of the Supplemental
-  Material).~\cite{mantegna_stochastic_1994}
+  Section~\ref{S-section:truncation} of the Supporting Information).~\cite{mantegna_stochastic_1994}
 
@@
 
-%BJC8: from author guidelines. Should there only be a line between column headings?
-%Use a single horizontal rule to separate the column headings from the entries in the table.
-Use horizontal space within the body of the table to separate broad groups of entries.
-Extra vertical space may be used between columns.
-Avoid vertical rules in tables.
-Use lower-case roman letters for footnotes placed at the bottom of a table.
-%MRS9: I'd go with what they said.  Looking at PRE, it looks like you can put double lines above and below the table, though - I added them 
   \begin{table*}[!htb]
@@
   distribution of dwell times are both characteristic of CTRWs
-  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}).  The
-  apparent anti-correlation between hops suggests a fractional diffusion
-  process is subordinate to the CTRW. Of the different models, a process
-  subordinated by FBM or FLM is best supported by the data because the
-  analytical correlation structures of hop lengths are close to those observed
-  in our simulations (Figure~\ref{fig:hop_acf}). Fractional motion is common
-  in crowded viscoelastic environments where motion is highly influenced by
-  the movement of surrounding components, such as monomer tails in our
-  case.~\cite{ernst_fractional_2012}
+  (See Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). 
+  %The apparent
+  Anti-correlation between hops suggests a fractional diffusion process is 
+  subordinate to the CTRW. Of the different models, a process subordinated by 
+  FBM or FLM is best supported by the data because the analytical correlation 
+  structures of hop lengths are close to those observed in our simulations 
+  (See Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). Fractional 
+  motion is common in crowded viscoelastic environments where motion is highly
+  influenced by the movement of surrounding components, such as monomer tails 
+  in our case.~\cite{ernst_fractional_2012}
 
@@
 
-  \begin{figure*}
-  \centering
-  % Next 3: /figures/sfbm_distributions
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
-  \caption{}\label{fig:hop_distribution_comparison}
-  \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
-  \caption{}\label{fig:powerlaw}
-  \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
-  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
-  \caption{}\label{fig:hop_acf}
-  \end{subfigure}
-  \caption{Using urea as an example, (a) the distribution of hop lengths can be
-	  fit by a Gaussian in addition to a more general L\'evy stable
-	  distribution, though the L\'evy stable distribution does a better job of
-	  capturing the heavier tails and increased density near 0. We explore
-	  models fit to both distributions, as Gaussian hops are more convenient
-	  to model. (b) The distribution of dwell times is fit well by a power
-	  law but it over-estimates the probability density at long dwell
-	  times. A power law truncated with an exponential cut-off better
-	  describes the probability of long dwell times in our simulations. (c)
-	  The hops are negatively correlated to their previous hop. In
-	  combination, (a) -- (c) support modeling solutes as either
-	  subordinated fractional Brownian or L\'evy motion. All other solutes
-	  show similar distributions and autocorrelation functions (see
-	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
-  }\label{fig:anticorrelated_hops}
-  \end{figure*}
+%  %BJCA: maybe this to supporting?
+%  %MRS: yeah, I think so. 
+%  \begin{figure}
+%  \centering
+%  % Next 3: /figures/sfbm_distributions
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
+%  \caption{}\label{fig:hop_distribution_comparison}
+%  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
+%  \caption{}\label{fig:powerlaw}
+%  \end{subfigure}
+%  \begin{subfigure}{0.325\textwidth}
+%  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
+%  \caption{}\label{fig:hop_acf}
+%  \end{subfigure}
+%  \caption{Using urea as an example, (a) the distribution of hop lengths can be
+%	  fit by a Gaussian in addition to a more general L\'evy stable
+%	  distribution, though the L\'evy stable distribution does a better job of
+%	  capturing the heavier tails and increased density near 0. We explore
+%	  models fit to both distributions, as Gaussian hops are more convenient
+%	  to model. (b) The distribution of dwell times is fit well by a power
+%	  law but it over-estimates the probability density at long dwell
+%	  times. A power law truncated with an exponential cut-off better
+%	  describes the probability of long dwell times in our simulations. (c)
+%	  The hops are negatively correlated to their previous hop. In
+%	  combination, (a) -- (c) support modeling solutes as either
+%	  subordinated fractional Brownian or L\'evy motion. All other solutes
+%	  show similar distributions and autocorrelation functions (see
+%	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
+%  }\label{fig:anticorrelated_hops}
+%  \end{figure}
 
@@
   to L\'evy stable distributions since it is more general than the Gaussian
-  distribution. We plotted the MLE fits of both on top of urea's hop length
-  distribution in Figure~\ref{fig:hop_distribution_comparison}. The L\'evy
-  distribution does a better job capturing the somewhat heavy tails and high
-  density near 0 of the hop length distribution. However, since there are no
-  known exact simulation techniques for generating realizations of fractional
-  L\'evy motion, this more general fit may not be worthwhile. In fact, we
-  typically observe very little difference between model predictions
-  parameterized with FLM versus FBM (see Figure~\ref{fig:anomalous_msds}).
+  distribution. We plotted the MLE fits of both on top of each solute's hop length
+  distribution in Figure~\ref{S-fig:anticorrelated_hops} of the
+  Supporting Information. The L\'evy distribution does a better job capturing
+  the somewhat heavy tails and high density near 0 of the hop length distributions. 
+  However, since there are no known exact simulation techniques for generating 
+  realizations of fractional L\'evy motion, this more general fit may not be 
+  worthwhile. In fact, we typically observe very little difference between model
+  predictions parameterized with FLM versus FBM.% (see Figure~\ref{fig:anomalous_msds}).
 
@@
   approach, we truncate the power law distribution with an exponential cut-off,
-  lowering the probability of extremely long dwell times. We demonstrate this
-  effect in the inset to Figure~\ref{fig:powerlaw}, where the density of the
-  truncated power law drops below that of the pure power law and tends towards
-  0 near a dwell time of 250 ns.
+  lowering the probability of extremely long dwell times. 
+  %We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where 
+  On long time scales, the density of the truncated power law drops below that
+  of the pure power law and tends towards 0. % near a dwell time of 250 ns.
 
@@
 
-  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}
-
-  We observe that in some cases, solute trajectories extracted from our MD
-  simulations display non-stationary behavior. We defined the perceived
-  equilibration time point for each solute based on the time at which the
-  number of solutes inside the pores and tails stabilized
-  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
-  evidence of non-stationary solute behavior after the perceived equilibration
-  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
-  the MSD of the solutes calculated using trajectory data from the first and
-  second halves of the ``equilibrated" simulation time. Ethylene glycol and
-  methanol show considerable differences between the MSDs of the two halves.
-  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
-  shapes of urea and acetic acid's MSD curves are also very similar (see
-  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
-
-  \begin{table}[h]
-  \centering
-  \begin{tabular}{|c|c|c|}
-  \hline
-  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
-                           & First Half       & Second Half      \\\hline
-  urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
-  ethylene glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
-  methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
-  acetic acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
-
-  \end{tabular}
-  \caption{In order to be considered stationary, the MSD of the ensemble of
-	  solute trajectories should be the same independent of the portion of
-	  equilibrated trajectory that is analyzed. The MSD values in this
-	  table are averages taken after a 500 ns time lag, calculated
-	  independently from the first and second halves of the equilibrated
-	  solute trajectories. Urea and acetic acid both appear to satisfy the
-	  stationarity criteria, while ethylene glycol and methanol show
-	  significantly smaller MSDs when calculated from the second half of
-	  the equilibrated trajectories.}\label{table:stationarity}
-  \end{table}
-
-  Given stationary data, the AD approach is capable of predicting solute MSDs
-  measured from MD simulations within or near statistical uncertainty. In
-  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized
-  the AD models using the first half of the stationary solute equilibrated
-  trajectories and then compared the model predictions to the MD MSD of the
-  second half of the stationary trajectories. In most cases, the model
-  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.
-
-  This brief analysis suggests that we may be operating on the border of the
-  minimum amount of data required to accurately parameterize AD approach
-  models. Working with only half of the data we collected ($\sim$ 2 $\mu$s
-  post-equilibration) may not always be sufficient for extracting reliable
-  parameter estimates. Therefore, for the remainder of this work, we will
-  employ parameters fit to the entire equilibrated portion of the solute
-  trajectories. Even doubling the data might not be good enough for molecules
-  with statistical non-stationarity, meaning the predictive and interpretive
-  power of the time series modeling applied to these trajectories will be
-  lower.
+  %BJCA: This section to supporting
+%  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}
+%  %MRS: yes, though report the results in main text.
+%
+%  We observe that in some cases, solute trajectories extracted from our MD
+%  simulations display non-stationary behavior. We defined the perceived
+%  equilibration time point for each solute based on the time at which the
+%  number of solutes inside the pores and tails stabilized
+%  (Figure~\ref{S-fig:equilibration}). With this definition, we observe
+%  evidence of non-stationary solute behavior after the perceived equilibration
+%  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
+%  the MSD of the solutes calculated using trajectory data from the first and
+%  second halves of the ``equilibrated" simulation time. Ethylene glycol and
+%  methanol show considerable differences between the MSDs of the two halves.
+%  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
+%  shapes of urea and acetic acid's MSD curves are also very similar (see
+%  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).
+%  
+%  \begin{table}[h]
+%  \centering
+%  \begin{tabular}{|c|c|c|}
+%  \hline
+%  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
+%                           & First Half       & Second Half      \\\hline
+%  urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
+%  ethylene glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
+%  methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
+%  acetic acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
+%
+%  \end{tabular}
+%  \caption{In order to be considered stationary, the MSD of the ensemble of
+%	  solute trajectories should be the same independent of the portion of
+%	  equilibrated trajectory that is analyzed. The MSD values in this
+%	  table are averages taken after a 500 ns time lag, calculated
+%	  independently from the first and second halves of the equilibrated
+%	  solute trajectories. Urea and acetic acid both appear to satisfy the
+%	  stationarity criteria, while ethylene glycol and methanol show
+%	  significantly smaller MSDs when calculated from the second half of
+%	  the equilibrated trajectories.}\label{table:stationarity}
+%  \end{table}
+%
+%  Given stationary data, the AD approach is capable of predicting solute MSDs
+%  measured from MD simulations within or near statistical uncertainty. In
+%  Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized
+%  the AD models using the first half of the stationary solute equilibrated
+%  trajectories and then compared the model predictions to the MD MSD of the
+%  second half of the stationary trajectories. In most cases, the model
+%  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.
+%  
+%  This brief analysis suggests that we may be operating on the border of the
+%  minimum amount of data required to accurately parameterize AD approach
+%  models. Working with only half of the data we collected ($\sim$ 2 $\mu$s
+%  post-equilibration) may not always be sufficient for extracting reliable
+%  parameter estimates. Therefore, for the remainder of this work, we will
+%  employ parameters fit to the entire equilibrated portion of the solute
+%  trajectories. Even doubling the data might not be good enough for molecules
+%  with statistical non-stationarity, meaning the predictive and interpretive
+%  power of the time series modeling applied to these trajectories will be
+%  lower.
 
@@
   parameterize AD models with all available data after the perceived
-  equilibration time. The MSD curves generated from both the one and 
-  two mode models are overlayed with the MD simulated MSDs for comparison in
-  Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
-  mode models are presented in Figures~\ref{fig:1mode_parameters}
-  and~\ref{fig:2mode_parameters}.
+  equilibration time.   
+  %BJCB: added next two sentences point towards non-stationarity discussion
+  We observe that in some cases, solute trajectories extracted from our MD
+  simulations may display non-stationary behavior. Our brief analysis 
+  in Section~\ref{S-section:msd_comparison} of the Supporting Information 
+  suggests that we may be operating on the border of the minimum amount of
+  data required to accurately parameterize AD approach models.
+  The MSD curves generated from both the one and two mode models are overlaid
+  with the MD simulated MSDs for comparison in Figure~\ref{fig:anomalous_msds}.
+  The associated parameters for the one and two mode models are presented in
+  Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.
 
@@
 
+  %MRS: some of these discussions might belong in the SI, with just the top line information in the main text.
+People don't really care about the details of the individual parameters, just what story that tells.
+  %BJCB: I think the figures need to stay though   
+  %MRSB: Hmm. I'm not entirely convinced, but we can leave it in for now and see what the reviewers think.
   \begin{figure*}
@@
   However, the modeled trajectories undershoot the mean MD MSD as the time lag
-  increases. As discussed in the previous section, long time positional
-  anti-correlation, on the order of hundreds of ns, may not exist in the MD
-  system. Eventual loss of correlation would result in a shift from sub-linear
-  to linear MSD behavior, as observed in the MD trajectories. Acetic acid
-  exemplifies this point. At first glance, acetic acid's predicted MSD appears
-  to match the curvature of MD quite well, but closer examination reveals that
+  increases. Long time positional anti-correlation, on the order of hundreds of
+  ns, may not exist in the MD system. Eventual loss of correlation would result 
+  in a shift from sub-linear, or subdiffusive, to linear, or diffusive, MSD behavior, as observed in the MD 
+  trajectories. Acetic acid exemplifies this point. At first glance, acetic acid's
+  predicted MSD appears to match the curvature of MD quite well, but closer 
+  examination reveals that
   the MD MSD curve may actually shift from a sub-linear to a linear regime around
@@
 
+  % BJCB: I might be able to get away with moving this paragraph to SI if I briefly
+  % mention the reason in the above paragraph.
   The two mode models display curvature more consistent with MD but for
   non-physical reasons. Every time a switch between the pores and tails occurs,
-  the width of the distribution used to model hops changes. We are unaware of
-  an appropriate technique which can correlate hops that come from different
-  hop distributions, therefore every time a mode switch occurs, the correlation
-  structure is broken. Solutes that switch between modes the least show
+  the width of the distribution used to model hops changes, and the correlation structure is broken. 
+  %MRSB: I cut below.
+  %We are unaware of
+  %an appropriate technique which can correlate hops that come from different
+  %hop distribution every time a mode switch occurs, the correlation
+  %structure is broken. 
+  Solutes that switch between modes the least show
   predicted MSDs with the greatest curvature. Due to the much larger
@@
   mode transitions are relatively rare and the predicted MSDs have significant
-  curvature. This artificially solves the problem of long timescale
-  correlation, however we do not recommend this as it has no physical basis.
-
+  curvature. This artificially resolves the problem of long timescale
+  correlation, however, it has no physical basis.
+
+  %MRS: this paragraph below may be the sort of summary of the models that would
+  %go in the main text, with the details in the SI.
   The model parameters for the one and two mode models tell stories about each
@@
 
+  %BJCB: maybe move the next two paragraphs to the SI?
+  %MRSB: I think that this is more useful in the main text, since it connects models to the simulations and the physics.
   Examining first the parameters of the one mode model, we can begin to break
@@
 
-  Urea spends the largest fraction of its time trapped via association with
+  % BJCB: I could summarize the four following paragraphs in terms of key
+  % takeaways, like you suggested with the AD model above.
+
+  %MRSB: I think people like the physical intuition gained. I added bullet points to aid reading. 
+  \begin{itemize}
+  \item \textit{Urea} spends the largest fraction of its time trapped via association with
   sodium ions. It does so 31\% of the total time while in the tails (state 3)
@@
 
-  Methanol spends most of its time unbound in the tail region (state 1) and
+  \item \textit{Methanol} spends most of its time unbound in the tail region (state 1) and
   spends a significant portion of time hydrogen bonded while in the tail
   region. Tail region hydrogen bonds are donated from methanol to the ether
-  linkages between the monomer head groups and tails. One might modify the
+  linkages between the monomer head groups and tails, as well as to the ester groups
+  at the ends of the tails. One might modify the
   rate of methanol transport by controlling its partition into the monomer
@@
   pronounced than that seen in the hop length distributions of the previous
-  section. We therefore did not consider the Gaussian case (see
-  Figure~\ref{fig:gaussian_levy_comparison}). The correlation structure
-  between hops is consistent with that of FLM (Figure~\ref{fig:msddm_acf}).
-  The parameters of the L\'evy stable distributions along with their Hurst
-  parameters are visualized in Figure~\ref{fig:msddm_parameters} (and tabulated
-  in the Supporting Information, Table~\ref{S-table:msddm_params}).
-
-  \begin{figure*}
-  \centering
-  \begin{subfigure}{0.49\textwidth}
-  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
-  \caption{}\label{fig:gaussian_levy_comparison}
-  \end{subfigure}
-  % /figures/msddm_acf.py
-  \begin{subfigure}{0.42\textwidth}
-  \includegraphics[width=\textwidth]{msddm_acf.pdf}
-  \caption{}\label{fig:msddm_acf}
-  \end{subfigure}
-  \caption{(a) The emission distributions of hop lengths are non-Gaussian and
-	  heavy-tailed. Shown here is the emission distribution for transitions
-	  between states. The maximum likelihood Gaussian fit severely
-	  underestimates the empirical density of hops near and far from zero
-	  while overestimating the density of hops at intermediate values. (b)
-	  Jumps drawn from the transition distribution are negatively
-	  correlated to each other. The normalized version of
-	  Equation~\ref{eqn:flm_autocovariance} fits well to the data
-	  suggesting FLM is an appropriate way to model jumps.}
-	  \label{fig:msddm_emissions}
-  \end{figure*}
-
+  section (see Figure~\ref{S-fig:gaussian_levy_comparison} of the Supporting
+  Information). We therefore did not consider the Gaussian case. The correlation
+  structure between hops is consistent with that of FLM (see 
+  Figure~\ref{S-fig:msddm_acf}). The parameters of the L\'evy stable distributions
+  along with their Hurst parameters are visualized in Figure~\ref{fig:msddm_parameters}
+  (and tabulated in the Supporting Information, Table~\ref{S-table:msddm_params}).
+
+  %BJCA: potentially move this to SI
+  %MRS: seems good.  Again, make sure that the conclusions are referenced in the main text. 
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.49\textwidth}
+%  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
+%  \caption{}\label{fig:gaussian_levy_comparison}
+%  \end{subfigure}
+%  % /figures/msddm_acf.py
+%  \begin{subfigure}{0.42\textwidth}
+%  \includegraphics[width=\textwidth]{msddm_acf.pdf}
+%  \caption{}\label{fig:msddm_acf}
+%  \end{subfigure}
+%  \caption{(a) The emission distributions of hop lengths are non-Gaussian and
+%	  heavy-tailed. Shown here is the emission distribution for transitions
+%	  between states. The maximum likelihood Gaussian fit severely
+%	  underestimates the empirical density of hops near and far from zero
+%	  while overestimating the density of hops at intermediate values. (b)
+%	  Jumps drawn from the transition distribution are negatively
+%	  correlated to each other. The normalized version of
+%	  Equation~\ref{eqn:flm_autocovariance} fits well to the data
+%	  suggesting FLM is an appropriate way to model jumps.}
+%	  \label{fig:msddm_emissions}
+%  \end{figure}
+
+  %MRSB: discussion of parameter specifics is a potential place to move.
   \begin{figure*}
@@
 
-  Despite their shortcomings, our mathematical models help us think about how
-  to design LLC monomers for solute-specific separations by forcing us to think
-  in terms of controlling solute transport. The anomalous diffusion modeling
-  approach is quite flexible because it does not require knowledge of specific
-  trapping mechanisms. Screening a set of solutes and applying the anomalous
-  diffusion approach can help uncover trapping mechanisms by forcing the
-  scientist to identify features common to solutes with long or short hop
-  lengths and dwell times. 
-  The MSDDM is a powerful way to characterize explicit
-  trapping mechanisms. It clearly partitions a trajectory into discrete
-  mechanisms and quantifies their relative dominance in the real system. For
-  example, it is clear that sodium ion association is primarily responsible for
-  trapping urea while hydrogen bonding dominates ethylene glycol. If one
-  re-designs an LLC monomer to eliminate one source of trapping, then 
-  higher selectivities may result. The modeling approaches presented in this paper 
-  facilitate new ways of approaching complex separation problems.
-
-  \section*{Supporting Information}
-
-  Detailed explanations and expansions upon the results and procedures
-  mentioned in the main text are described in the Supporting Information. This
-  information is available free of charge via the Internet at
-  http://pubs.acs.org.
+%  Despite their shortcomings, our mathematical models help us think about how
+%  to design LLC monomers for solute-specific separations by forcing us to think
+%  in terms of controlling solute transport. The anomalous diffusion modeling
+%  approach is quite flexible because it does not require knowledge of specific
+%  trapping mechanisms. Screening a set of solutes and applying the anomalous
+%  diffusion approach can help uncover trapping mechanisms by forcing the
+%  scientist to identify features common to solutes with long or short hop
+%  lengths and dwell times. The MSDDM is a powerful way to characterize explicit
+%  trapping mechanisms. It clearly partitions a trajectory into discrete
+%  mechanisms and quantifies their relative dominance in the real system. For
+%  example, it is clear that sodium ion association is primarily responsible for
+%  trapping urea while hydrogen bonding dominates ethylene glycol. If one
+%  re-designs an LLC monomer to eliminate one source of trapping, then 
+%  higher selectivities may result. The modeling approaches presented in this paper 
+%  facilitate new ways of approaching complex separation problems.
+
+  In a broader context, it is clear that time series modeling may be a useful way
+  to form a clear connection between complex solute dynamics on the nanosecond 
+  timescale and macroscopic observables. On the nanoscopic scale, one can both 
+  learn and characterize dynamical modes in order to identify areas of potentially
+  impactful molecular-level design changes. For example, it may be possible to 
+  modify solute transport rates and selectivities in LLC membranes by redesigning 
+  the LLC monomers to mitigate or enhance their chemically dependent interactions
+  with different solutes. With these models, dynamics can be propagated onto much 
+  longer time with computational ease. This allows one not only to predict a 
+  macroscopic observable for a specific system, but to explicitly calculate the 
+  effect of perturbations to model parameters that may result from a monomer 
+  design change. Overall, we hope that this work can advance the reader's 
+  understanding of how one can apply time series analysis in order to understand 
+  complex diffusive behavior in any system of interest.
+
+%  \section*{Supporting Information}
+%
+%  Detailed explanations and expansions upon the results and procedures
+%  mentioned in the main text are described in the Supporting Information. This
+%  information is available free of charge via the Internet at
+%  http://pubs.acs.org.
 
@@
 
+  \section*{Supporting Information}
+
+  \input si_arxiv_v2.tex
+
+  \clearpage
   %\bibliographystyle{apsrev4-2}
@@
   % No TOC image in PRE
-  %\section*{TOC Graphic}
-
-  %\begin{figure}[!htb]
-  %\centering
-  %\includegraphics[width=3.25in]{toc.pdf}
-  %\end{figure}
+%  \section*{TOC Graphic}
+%    
+%  \begin{figure}[!htb]
+%  \centering
+%  \includegraphics[width=3.25in]{toc.pdf}
+%  \end{figure}
 

### 2020-05-07 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
Filling in missing parts of draft

--- 2020-04-29 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
@@
 
-	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia
-        and Michael R.  Shirts, for consideration for publication as
-        an Article in the Journal of Chemical Theory and
-        Computation. We expect this work to be of significant interest
-        to researchers who study complex transport at the molecular
-        level, as it describes important new approaches for estimating long
-        time scale behavior and bulk transport behavior from shorter
-        molecular trajectories exhibiting anomalous diffusion rather
-        than Brownian motion. Please note that this article has been
-        uploaded to arXiv with differences only in formatting:
-        \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\
+	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael 
+	R.  Shirts, for consideration for publication as an Article in the Journal
+	of Chemical Theory and Computation. We expect this work to be of significant
+	interest to researchers who study complex transport at the molecular level,
+	as it describes important new approaches for estimating long time scale 
+	behavior and bulk transport behavior from shorter molecular trajectories 
+	exhibiting anomalous diffusion rather than Brownian motion. Please note 
+	that this article has been uploaded to arXiv with differences only in 
+	formatting: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\        
+%        Please note that the content of this article
+%        %BJC: see if you agree with these changes
+%        has been uploaded to arXiv: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}.
+%        For submission to JCTC, we have made minor changes to the introduction,
+%        abstract and conclusion in order to make it more suited for readers of 
+%        the journal. We also made efforts to shorten the manuscript by moving 
+%        certain discussions and figures to the supporting information. \\
 
-	In this article, we analyze solute trajectories generated from
-        5$\mu$s molecular dynamics (MD) simulations of an inverted
-        hexagonal (H\textsubscript{II}) phase self-assembled lyotropic
-        liquid crystal (LLC) polymer membrane to parameterize two
-        different stochastic time series approaches capable of
-        predicting solute flux and selectivity on a macroscopic
-        scale. Both approaches quantitatively reproduce the mean
-        squared displacements (MSDs) exhibited by solutes in MD
-        simulations. This is among the first studies to apply time
-        series modeling of molecular simulations in order to infer
-        behavior at long time scales and estimate bulk
-        materials properties with complex anomalous diffusion
-        mechanisms.\\
+    In this work, we build on the chemical intuition gained from our previous 
+    study (Coscia and Shirts \textit{J. Phys.  Chem. B}, 123, 6314--6330 (2019))
+    in order to formulate two different stochastic time series modeling approaches,
+    %which produce trajectory realizations that share the same dynamical properties as 
+    %those exhibited by solutes in our 5~$\mu$s molecular dynamics (MD) simulations.
+    parameterized from 5~$\mu$s molecular dynamics (MD) simulations, capable of 
+    predicting solute flux and selectivity on a macroscopic scale. 
+    First, using anomalous diffusion theory, we parameterize solute motion as 
+    subordinated fractional Brownian and L\'evy motion processes, based on the 
+    observation that solutes experience a series of dwell times separated by
+    anti-correlated hop lengths. Secondly, we add state-dependent dynamics to 
+    standard Markov state modeling approaches, where we model solute motion as 
+    a series of transitions between various trapped states, each with different
+    dynamical properties. We demonstrate how one can project these models 
+    onto macroscopic timescales in order to estimate solute flux and selectivity.
+    This is among the first studies to apply time series modeling of molecular 
+    simulations in order to infer behavior at long time scales and estimate bulk
+    materials properties with complex anomalous diffusion mechanisms.
 
-	This article builds on recent work of ours published in
-        J. Phys. Chem. B where we characterized transport mechanisms
-        exhibited by a series of small polar solutes in an LLC
-        Membrane (Coscia and Shirts \textit{J. Phys.  Chem. B}, 123,
-        6314--6330 (2019)). In this work, we build on the chemical
-        intuition gained from our previous study in order to formulate
-        stochastic models which produce trajectory realizations that
-        share the same dynamical properties as those exhibited by
-        solutes in our MD simulations. We explore two main modeling
-        approaches. First, using anomalous diffusion theory, we
-        parameterize solute motion as subordinated fractional Brownian
-        and L\'evy motion processes, based on the observation that
-        solutes experience a series of dwell times separated by
-        anti-correlated hop lengths. Secondly, we add state-dependent
-        dynamics to standard Markov state modeling approaches, where
-        we model solute motion as a series of transitions between
-        various trapped states, each with different dynamical
-        properties.  Finally, we demonstrate how one can project models 
-        onto macroscopic timescales in order to estimate
-        solute flux and selectivity.\\
+%	In this article, we analyze solute trajectories generated from 5~$\mu$s molecular 
+%	dynamics (MD) simulations of an inverted hexagonal (H\textsubscript{II}) phase self-assembled lyotropic
+%        liquid crystal (LLC) polymer membrane to parameterize two
+%        different stochastic time series approaches capable of
+%        predicting solute flux and selectivity on a macroscopic
+%        scale. Both approaches quantitatively reproduce the mean
+%        squared displacements (MSDs) exhibited by solutes in MD
+%        simulations. This is among the first studies to apply time
+%        series modeling of molecular simulations in order to infer
+%        behavior at long time scales and estimate bulk
+%        materials properties with complex anomalous diffusion
+%        mechanisms.\\
+%
+%	This article builds on recent work of ours published in
+%        J. Phys. Chem. B where we characterized transport mechanisms
+%        exhibited by a series of small polar solutes in an LLC
+%        Membrane (Coscia and Shirts \textit{J. Phys.  Chem. B}, 123,
+%        6314--6330 (2019)).  We explore two main modeling
+%        approaches. First, using anomalous diffusion theory, we
+%        parameterize solute motion as subordinated fractional Brownian
+%        and L\'evy motion processes, based on the observation that
+%        solutes experience a series of dwell times separated by
+%        anti-correlated hop lengths. Secondly, we add state-dependent
+%        dynamics to standard Markov state modeling approaches, where
+%        we model solute motion as a series of transitions between
+%        various trapped states, each with different dynamical
+%        properties.  Finally, we demonstrate how one can project models 
+%        onto macroscopic timescales in order to estimate
+%        solute flux and selectivity.\\
 
@@
 		and transport under confinement within various nanostructured materials 
-		(Northeastern University, 617-373-8619,\\ \href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})
+		(Northeastern University, 617-373-8619,\\ \href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu}).
 
@@
 		including work on ion transport in various ordered liquid crystalline phases. 
-		(University of Minnesota, 612-625-4599, \href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})
+		(University of Minnesota, 612-625-4599, \href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu}).
 
@@
 		proton transport in nanostructured and charged polymer membranes. (The University of Tennessee 
-		Knoxville, 865-974-2026, \href{mailto:spaddison@utk.edu}{spaddison@utk.edu})
+		Knoxville, 865-974-2026, \href{mailto:spaddison@utk.edu}{spaddison@utk.edu}).
+
+		\item Coray Colina uses various simulation techniques to understand structure-property relations
+		in functional materials including nanoporous materials for separation applications. (University
+		of Florida, 352-294-3488, \href{mailto:colina@chem.ufl.edu}{colina@chem.ufl.edu}).
+
+		\item Venkat Ganesan uses multiscale modeling to study solute and ion transport in complex
+		nanostructured morphologies in order to learn how to design novel materials. (The University
+		of Texas at Austin, 512-471-4856, \href{mailto:venkat@che.utexas.edu}{venkat@che.utexas.edu}).
+
+%		\item Ralf Metzler is an expert in anomalous stochastic processes, with interest in the physical
+%		origins of anomalous diffusion as well as the inference of the parameters which govern these
+%		processes. (Universität Potsdam, +49 331 977 5715, \href{mailto:rmetzler@uni-potsdam.de}{rmetzler@uni-potsdam.de}).
 

### 2020-05-08 Ben_Manuscripts/hdphmm/Draft.tex
Comments on draft.

@@
   \begin{abstract}
-
-  Appropriate time series modeling of complex diffusion on the microsecond time scale
+  %MRS: added ``in soft matter systems'' to make it clear that the focus on understanding things in physical systems.
+  Appropriate time series modeling of complex diffusion in soft matter systems on the microsecond time scale
   can provide a path towards inferring transport mechanisms and predicting bulk properties
@@
   number of distinct latent vector autoregressive dynamical modes. 
-
+  %MRS: in above sentence: try to rephrase around the physical information obtained (mechanism or properties) rather than the mathematical route to it.
+
+  %MRS: below - it's not the solute behavior, though, it's states identified by them model. Rephrase?
   We group similar solute behavior into clusters, analyze the dynamics characteristic
@@
   Overall, this work provides an effective way to simultaneously identify transport 
-  mechanisms and project complex diffusive behavior on long time scales.
+  mechanisms 
+  %MRS: emphasizing things, not just analysis.
+  in porous nanoscale materials
+  and project complex diffusive behavior on long time scales.
 
@@
   % delete this paragraph and start with the next one. 
+  % MRS: going to JPC, so emphasize the physical systems.
   There is a need for highly selective membranes in order to perform efficient 
@@
   with macroscopic observables.
+  %MRS: should explicitly point out that just calculating diffusion coefficients don't work for subdiffusive behavior, so
+  %MRS need a different way to do it.
   \begin{itemize}
@@
 
+  %MRS: point out that LLC's are examples where there are lots of hopping/jumping (cite previous papers) and
+  %MRS: so we need different approaches.
   In this work, we are particularly interested in the design of lyotropic liquid crystal (LLC)
@@
   \begin{itemize}
-    \item The IHMM has not been used much for MD trajectory analysis.
+    %MRS: start with where it has been used before (to establish utility) a
     \item It's been used extensively for speaker diarization and has found some application
     in single particle trajectory analysis.
+    %MRS: Then say it hasn't been used in this context (do we know of any, if not say so).
+    \item The IHMM has not been used much for MD trajectory analysis.
+
   \end{itemize}
@@
   transport mechanisms which give rise to different solute dynamical behavior.
-  Second, we want to evaluate the ability of our model to reproduce solute trajectories
-  in a stochastic manner so that we can use it to predict macroscopic transport 
-  properties which would otherwise require much longer MD simulations.
+  %MRS: flipping for clarity.
+  %Second, we want to evaluate the ability of our model to reproduce solute trajectories
+  %in a stochastic manner so that we can use it to predict macroscopic transport 
+  %properties which would otherwise require much longer MD simulations.
+  Second, we want to predict macroscopic transport by using our model to generate 
+  stochastic solute trajectories at much longer timescales than possible with MD simulations, 
+  extending into timescale where diffusive behavior again occurs.
 
@@
 
+  %MRS: consider added subsubsections to make it more readable.
   Hidden Markov models (HMMs) are a useful and widely used technique for modeling
@@
   and $\Sigma$ parameters in segments with a relatively low number of emissions.
-  In these cases, the mean in each dimension tends to be a more reliable indicator of
+  In these cases, 
+  %MRS: maybe plateauing of the mean below?  Be more precise.
+  the mean in each dimension tends to be a more reliable indicator of
   convergence (see Figure~\ref{S-fig:convergence3d} of the Supporting Information).
@@
   We reparameterized the time series, preserving the state sequence, in terms
-  of the radial and axial coordinates ($r$, $z$) because $x$ and $y$ aren't 
-  meaningful alone due to the system's radial symmetry. We converted the $x$ and 
+  of the radial and axial coordinates ($r$, $z$) 
+  %MRS: not needed.
+  %because $x$ and $y$ aren't meaningful alone 
+  due to the system's radial symmetry. We converted the $x$ and 
   $y$ center-of-mass coordinates to $r$. We fixed the state sequence from the 
@@
   Therefore, we only ran the inference procedure for 100 iterations. 
+  %MRS: hmm. Here the new covariance parameters is redone in r - does there need to be any transformation applied? 
+  %MRS: though might be OK, since x^2 + y^2 = r^2 so maybe covariance are additive if x and y uncorrelated (which they should be)
   %However, note that the uncertainty in their
@@
 
-  We defined the finalized parameters of each state as the average of the parameters 
+  We defined the final parameters of each state as the mean of the parameters 
   from each iteration recorded after the equilibration time point. We found the 
@@
 
+  %MRS: maybe add subsubsections naming/labeling each part of the process so that people have a sense of the steps,
+  %MRS: makes it easier to read.
   We clustered like parameter sets in order to reduce the state space to
@@
   of the Supporting Information).
+  %MRS: not clear what the consequence of the above is?
 
@@
   dwell times approach infinity as $T_{ii}$ approaches 1. There we found the most success with
-  agglomerative clustering by linearizing this relationship and clustering on $-log(1 - T_{ii})$
+  agglomerative clustering by linearizing this relationship and clustering on $-\log(1 - T_{ii})$
   (see Section\ref{S-section:selfT_cluster} of the Supporting Information for a graphical
@@
   this may seem like a high number of states, many are sampled infrequently.
+  %MRS: what is the consequence of being sampled infrequently.
 
@@
 
+  %MRS: maybe ``using the parameterized model to explore mechanisms''
   \subsection{Tools for Exploring Mechanisms}\label{method:interactions}
@@
 
-  We developed a way to measure the local density of the membrane at arbitrary
-  points in the unit cell. We histogrammed the positions in three dimensions
+  %We developed a way to 
+  We measure the local density of the membrane at arbitrary
+  points in the unit cell as follows. We histogrammed the positions in three dimensions
   Since our system is in a monoclinic unit cell, we periodically replicated
@@
   behavior exhibited by solutes over long MD trajectories in terms of 
-  solute-membrane interactions. Further, we can use the IHMM in order to generate
+  solute-membrane interactions. In addition, we can use the IHMM in order to generate
   stochastic trajectories, with dynamics similar to MD, so that we can estimate 
   macroscopic transport properties. 	
+  %MRS: subsection lettering is really big - makes it seem like a very different section?
 
@@
 
+  %MRS: maybe phrase it around types of mechanism, and use methanol as an example.
   \subsubsection*{The Dynamics of Methanol}
@@
   \end{subfigure}
+  %MRS: a lot of this caption test is duplicated from the main text. I would suggest reducing the duplication.
   \caption{(a) We can learn a significant amount of detail about solute motion by viewing 
@@
   mean. One could argue that the parameters of states 3--7 are actually very close which
-  suggests that solutes might behave alike in topologically distinct regions of the 
+  suggests that solutes might behave alike in 
+  %MRS: changed word.
+  %topologically 
+  morphologically
+  distinct regions of the 
   membrane.
@@
   surprisingly, both states 3 and 5 correspond to solutes located close to a pore center,
-  where one might expect solute motion to be less restricted. Although solutes in states
+  where one might expect solute motion to be less restricted. 
+  %MRS: are thsse h-bonding states?
+  Although solutes in states
   4 and 6 are in the viscous tail region, their dwell times are only intermediate. This
@@
   \end{subfigure}
+  %MRS: a lot of text here in the caption - think about reducing duplication with the text, and moving some to the text.
   \caption{We can learn the most about methanol's behavior by studying the dynamics
@@
   occur close to the pore centers. States 2, 4 and 6 occur well within the tail region of the membrane.
-  (c) Using the transition probabilities (p), we estimated the average time spent within each 
+  (c) Using the transition probabilities ($p$), we estimated the average time spent within each 
   of the states using 1000 simulations of a Bernoulli process where we continued to draw until transitioning
-  out of the state with probability 1 - p. Of the prevalent states, states 1 and 
+  out of the state with probability $1 - p$. Of the prevalent states, states 1 and 
   2 exhibit the shortest dwell times alongside their high covariances. States 5 and 7 have the longest dwell times in the pore and tail regions respectively.
@@
   groups and ether linkages. States with radial means greater than 1 nm (states 2,
-  4, 6 and 7) tend to hydrogen bond with the monomer tails. In the past we've shown
-  that there is a gradual transition from the hydrophilic to hydrophobic region in
-  these membranes, meaning the monomer location is not tightly bound in $r$. Therefore,
-  there are instances of hydrogen bond interactions that one might consider 
+  4, 6 and 7) tend to hydrogen bond with the monomer tails. 
+  %MRS: tweak
+  %In the past we've 
+  Our previous work has
+  shown that there is a gradual transition from the hydrophilic to hydrophobic region in
+  these membranes, meaning the monomer location is not tightly bound in $r$. 
+  %MRS: above logic is not clear?
+  Therefore, there are instances of hydrogen bond interactions that one might consider 
   uncharacteristic based on the state's radial mean.
+  %MRS: what is implication of ``uncharacteristicness''?
 
@@
   \end{subfigure}
+  %MRS: legend doesn't show stripes.
   \caption{(a) Methanol hydrogen bonds in different segments of the LLC monomer
@@
   % some discussion of this to previous section.
-  %MRS7: methanol yellow is hard to see in c)
+  %MRS: methanol yellow is hard to see in (b). Maybe add outlines to histogram?  I guess they are, increase alpha or something for yello?
+  %MRS: check consistency of capitalization in legend in (c) 
   \caption{(a) Solutes hydrogen bond and associate with sodium ions
@@
 
+  %MRS: maybe makes sense to talk a little about what features/parameters of the models the MSD is sensitive to?
   %BJC5: something we can do for the supporting information to show that this approach is valid: Eliminate nonidealities in our MD trajectories (compared to a pure VAR process) and use toy data to generate trajectories based on some number of states with different parameters.
@@
   characterized by hopping and trapping. The IHMM is a powerful approach for 
-  understanding particle motion as well as for generating cheap models
+  understanding particle motion as well as for generating inexpensive models
   which can give macroscopic insight.

### 2020-05-09 Ben_Manuscripts/hdphmm/Draft.tex
New figures, additions and organization to draft

@@
 
+\SectionNumbersOn
+
 \title{Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
@@
   \begin{abstract}
-  %MRS: added ``in soft matter systems'' to make it clear that the focus on understanding things in physical systems.
-  Appropriate time series modeling of complex diffusion in soft matter systems on the microsecond time scale
-  can provide a path towards inferring transport mechanisms and predicting bulk properties
-  characteristic of much longer time scales. In this work we apply the infinite hidden 
-  Markov model (IHMM) to solute center-of-mass trajectories generated from long 
-  molecular dynamics simulations in a cross-linked inverted hexagonal phase lyotropic 
-  liquid crystal (LLC) membrane in order to automatically detect and parameterize an unknown 
-  number of distinct latent vector autoregressive dynamical modes. 
+
+  Appropriate time series modeling of complex diffusion in soft matter systems on the
+  microsecond time scale can provide a path towards inferring transport mechanisms and
+  predicting bulk properties characteristic of much longer time scales. In this work 
+  we apply the infinite hidden Markov model (IHMM) to solute center-of-mass trajectories
+  generated from long molecular dynamics simulations in a cross-linked inverted hexagonal
+  phase lyotropic liquid crystal (LLC) membrane in order to automatically detect a
+  variety of solute dynamical states which can be further explained in terms of 
+  solute-membrane interactions.
+% order to automatically detect and parameterize an unknown number of
+%  latent vector autoregressive dynamical modes. 
   %MRS: in above sentence: try to rephrase around the physical information obtained (mechanism or properties) rather than the mathematical route to it.
+  %BJC2: gave a try
 
   %MRS: below - it's not the solute behavior, though, it's states identified by them model. Rephrase?
-  We group similar solute behavior into clusters, analyze the dynamics characteristic
-  to each cluster and relate them to physical interactions between solutes and the 
-  membrane. This enhancement to our understanding of the diverse range of influential 
-  solute-membrane interactions allows us hypothesize design changes to LLC monomers 
-  aimed towards controlling the rates of solute passage, thus improving the selective 
-  performance of LLC membranes.
+  %BJC2: I think this is better?
+  We group the states identified by the IHMM into clusters based on multiple metrics
+  aimed at distinguishing solute behavior based on their fluctuations, dwell times
+  in each state and position within the inhomogeneous membrane structure. We analyze
+  prevalent clusters in order to relate their parameters to physical interactions between 
+  solutes and the membrane. This enhancement to our understanding of the diverse range 
+  of influential solute-membrane interactions allows us to hypothesize design changes 
+  to LLC monomers aimed towards controlling the rates of solute passage, thus improving 
+  the selective performance of LLC membranes.
 
@@
   Overall, this work provides an effective way to simultaneously identify transport 
-  mechanisms 
-  %MRS: emphasizing things, not just analysis.
-  in porous nanoscale materials
-  and project complex diffusive behavior on long time scales.
+  mechanisms in 
+  %BJC2: porous nanoscale to nanoporous? 
+  %porous nanoscale 
+  nanoporous materials and project complex diffusive behavior on
+  long time scales.
 
@@
 
-  % BJC: Not sure if this should be the first paragraph, or if I could just
-  % delete this paragraph and start with the next one. 
   % MRS: going to JPC, so emphasize the physical systems.
@@
 
-  The ability to efficiently design novel membrane materials for selective separations would be 
-  greatly enhanced by easily interpretable methods for connecting microscopic fluctuations
-  with macroscopic observables.
+  The ability to efficiently design novel membrane materials for selective separations
+  would be greatly enhanced by easily interpretable methods for connecting microscopic
+  fluctuations with macroscopic observables.
   %MRS: should explicitly point out that just calculating diffusion coefficients don't work for subdiffusive behavior, so
   %MRS need a different way to do it.
+  %BJC2: added last two bullet points
   \begin{itemize}
@@
   	between theory and application.
-  	%BJC: this could potentially be moved further down
-  	\item There are two main challenges associated with this goal.
-  	%since complex and
-  	%diverse diffusive motion on time scales accessible to molecular simulations prevents
-  	%us from easily relating chemically dependent solute motion to experimental time scales.
-  	\item First, we need a simple way to identify and parameterize the fluctuations
-  	characteristic to dominant solute-membrane interactions.
-  	\item Second, we need a way to propagate this behavior far beyond the time scales
-  	afforded by MD.
+  	\item In many systems, it's possible to achieve this by calculating diffusion 
+  	constants.\cite{}
+  	\item Unfortunately, for systems which exhibit complex subdiffusive dynamics on the
+  	time scales accessible to MD simulation, one cannot calculate reliable diffusion 
+  	constants since solute mean square displacements (MSDs) are non-linear.
+  	\item Therefore, we are in need of a more flexible approach for modeling solute 
+  	dynamics which makes less assumptions about the solute's average behavior.
+  	%BJC2: I'm moving these towards the end
+%  	\item There are two main challenges associated with this goal.
+%  	%since complex and
+%  	%diverse diffusive motion on time scales accessible to molecular simulations prevents
+%  	%us from easily relating chemically dependent solute motion to experimental time scales.
+%  	\item First, we need a simple way to identify and parameterize the fluctuations
+%  	characteristic to dominant solute-membrane interactions.
+%  	\item Second, we need a way to propagate this behavior far beyond the time scales
+%  	afforded by MD.
   \end{itemize}
@@
   %MRS: so we need different approaches.
+  %BJC2: added last bullet point to lead in to following paragraph
   In this work, we are particularly interested in the design of lyotropic liquid crystal (LLC)
@@
 	design with measurable quantities.
+	\item This goal is complicated by the non-Brownian hopping and trapping behavior
+	induced by the membrane's diverse topology and inhomogeneous structure.~\cite{coscia_understanding_2019,coscia_chemically_2019}
   \end{itemize}
@@
   questions with this work. 
-  %BJC: this may be redundant from the second paragraph. Maybe better suited here?
   First, we want
@@
   transport mechanisms which give rise to different solute dynamical behavior.
-  %MRS: flipping for clarity.
-  %Second, we want to evaluate the ability of our model to reproduce solute trajectories
-  %in a stochastic manner so that we can use it to predict macroscopic transport 
-  %properties which would otherwise require much longer MD simulations.
   Second, we want to predict macroscopic transport by using our model to generate 
@@
   \end{itemize}
-
-%  Because independent solute trajectories generated by MD simulations share 
-%  similar state dynamics, we can use the IHMM to generate stochastic trajectory 
-%  realizations which sample from all behavior exhibited by MD. We verify that our
-%  stochastic realizations reproduce the expected hopping and trapping behavior 
-%  exhibited by MD. We quantitatively validate these trajectories by comparing 
-%  their mean squared displacement (MSD) to those measured by MD.
-
-%
-%%  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.
-%%  \begin{itemize}
-%%    \item 
-%%  \end{itemize}
-%
-%  There are limits to what we can learn from experiment about LLC membrane design.
-%  \begin{itemize}
-%    \item Experimental observables like permeability and selectivity allow us to speculate
-%    about the molecular origins of separation processes.
-%    %MRS2: not quite sure what you mean below?
-%    \item This drives an empirical design approach which can potentially neglect key
-%    interactions which influence selectivity.
-%    \item LLC membranes have been shown to exhibit selectivities which cannot be fully 
-%    explained by relatively simple macroscopic models. 
-%  \end{itemize}
-%  
-%  Molecular Dynamics (MD) simulations can give us mechanistic insights with atomistic 
-%  resolution so that we can intelligently design new membranes for solute-specific 
-%  separations.
-%  \begin{itemize}
-%    \item In our previous work, we built a detailed atomistic model which we used
-%    to understand the nanoscopic structure of an LLC Membrane.~\cite{coscia_understanding_2019}
-%    \item We also used the model in order to gain a qualitative understanding of 
-%    trapping mechanisms which lead to subdiffusive transport behavior.~\cite{coscia_chemically_2019}
-%  \end{itemize}
-%
-%  Unfortunately, the timescales that we can simulate with MD are insufficient to be
-%  able to make well-converged predictions of macroscopic transport properties 
-%  traditionally used to characterize membranes in the lab.
-%  \begin{itemize}
-%    %MRS2: would be good to get this next point into the first line of a paragraph, since it's quite important. 
-%    \item However, if we use descriptive stochastic models that can capture solute
-%    dynamics, then we could project long timescale behavior in addition to gaining
-%    a deeper understanding of solute behavior on short timescales. 
-%  \end{itemize}
 
@@
 
-  %MRS: consider added subsubsections to make it more readable.
+  %BJC2: I left section numbers off
+  \subsubsection*{Extending Hidden Markov Modeling to an Unknown Number of States}
+
   Hidden Markov models (HMMs) are a useful and widely used technique for modeling
@@
 
-  We describe the dynamics of each state visited by solutes using a first order vector 
-  autoregressive (VAR(1)) model. In general, a VAR($r$) process is characterized by a
+  \subsubsection*{Parameterizing the Hidden States}\label{method:var_params}
+
+  We describe the dynamics of each state visited by solutes in our MD simulations using
+  a first order vector autoregressive (VAR(1)) model. In general, a VAR($r$) process is characterized by a
   vector of observations in a time series that are linearly dependent on $r$ previous
@@
 
+  \subsubsection*{Applying the IHMM to MD Trajectories}
+
   Using the IHMM framework, we estimated the most likely sequence of hidden states in
@@
   We created a python implementation of this process which we heavily adapted from
-  %BJC: fox_bayesian is citation Emily Fox asked me to use.
   the MATLAB code of Fox et al.~\cite{fox_bayesian_2010} Parameter estimation is iterative. 
-  Therefore, we looked for convergence of each entry in the $\mathbf{c}$ vector as well
-  as the $A$ and $\Sigma$ matrices of Equation~\ref{eqn:var}. We detected equilibration 
-  of the parameters using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} on
-  the time series of parameter estimates. Plots illustrating parameter convergence are 
+  Therefore, we looked for convergence of the parameters in Equation~\ref{eqn:var}.
+  % each entry in the $\mathbf{c}$ vector as well as the $A$ and $\Sigma$ matrices of Equation~\ref{eqn:var}. 
+  We detected equilibration 
+  of the parameters using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
+  on the time series of parameter estimates. Plots illustrating parameter convergence are 
   available in Section~\ref{S-section:convergence} of the Supporting Information. We 
@@
 
-  %BJC: This paragraph could probably be cut down quite a bit. Leave justification for SI
+  %BJC2: I say 'applied' a lot. Diversity that eventually
   We carefully applied the IHMM algorithm in a way which takes advantage of the
   system's cylindrical symmetry. While there
-  %There 
   are a number of viable ways in which one could choose to analyze these time series,
-  %BJC: cutting down on verbosity
-  % We could use all 3 dimensions straight
-  %from the output trajectory. We could use just the $z$ dimensional coordinate 
-  %since we are primarily interested in through-plane membrane transport. Ultimately, 
   we chose to use a multi-step procedure that we believe adequately distinguishes 
@@
   pore center as the origin, we represented the radial distance of each solute's 
-  center-of-mass from the pore center in 2 dimensions, $x$ and $y$.
-  %(see Figure~\ref{fig:cartesian_cylinder}). 
-  By working in Cartesian coordinates, we avoid
-  mathematical complexity introduced by cylindrical coordinates while estimating the 
-  state sequence.
-
-% BJC6: I don't think this figure is necessary
-%  \begin{figure}
-%  \centering
-%  %MRS3: does this preserve the z-axis symmetry? Is it just ensuring
-%  %that you can't jump that far, or is it limiting the values that
-%  %the mean can take? Apologies if it's not clear to me yet.  I'm
-%  %pretty sure it's just limiting the jump (since y_t = c + f(y_t-1)),
-%  %but would be good to make that explicit - ``i.e. we need to make sure it doesn't jump too far'')
-%  %BJC5: preserving z-axis symmetry isn't needed yet at this stage. I use the
-%  % means in z in order to distinguish states (specifically estimating the c vector).
-%  % I get the radial means this way. Then just ignore z later.
-%  \includegraphics[width=0.2\textwidth]{cartesian_cylinder.pdf}
-%  \caption{Using the nearest pore center as the origin, we represented the solute's
-%  location along the pore axis in terms of the $z$ coordinates and their radial distance
-%  from the pore centers in 2 dimensions, $x$ and $y$.}\label{fig:cartesian_cylinder}
-%  \end{figure}
+  center-of-mass from the pore center in 2 dimensions, $x$ and $y$. By working in 
+  Cartesian coordinates, we avoid mathematical complexity introduced by cylindrical 
+  coordinates while estimating the state sequence.
 
@@
   outline our method for choosing reliable prior parameters.
-%  The entries of $A$ and $\Sigma$ do 
-%  not vary over a wide range, so the final parameters were relatively insensitive
-%  to their priors.
 
@@
   and $\Sigma$ parameters in segments with a relatively low number of emissions.
-  In these cases, 
-  %MRS: maybe plateauing of the mean below?  Be more precise.
-  the mean in each dimension tends to be a more reliable indicator of
+  In these cases, plateauing of the mean in each dimension tends to be a more reliable indicator of
   convergence (see Figure~\ref{S-fig:convergence3d} of the Supporting Information).
@@
   We reparameterized the time series, preserving the state sequence, in terms
-  of the radial and axial coordinates ($r$, $z$) 
-  %MRS: not needed.
-  %because $x$ and $y$ aren't meaningful alone 
-  due to the system's radial symmetry. We converted the $x$ and 
-  $y$ center-of-mass coordinates to $r$. We fixed the state sequence from the 
-  3D parameterization and applied the inference component of the IHMM procedure
-  to the cylindrical trajectories in order to estimate the VAR(1) parameters in
-  terms of $r$ and $z$. Since we fixed the state sequence, and we are using conjugate
-  priors, the VAR parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}).
+  of the radial and axial coordinates ($r$, $z$) due to the system's radial 
+  symmetry. We converted the $x$ and $y$ center-of-mass coordinates to $r$. 
+  We fixed the state sequence from the 3D parameterization and applied the 
+  inference component of the IHMM procedure to the cylindrical trajectories 
+  in order to estimate the VAR(1) parameters in terms of $r$ and $z$. Since
+  we fixed the state sequence, and we are using conjugate priors, the VAR 
+  parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}).
   Therefore, we only ran the inference procedure for 100 iterations. 
-  %MRS: hmm. Here the new covariance parameters is redone in r - does there need to be any transformation applied? 
-  %MRS: though might be OK, since x^2 + y^2 = r^2 so maybe covariance are additive if x and y uncorrelated (which they should be)
-  %However, note that the uncertainty in their
-  %estimates are a function of the number of data points used in their estimate.
+  % MRS: hmm. Here the new covariance parameters is redone in r - does there need to be any transformation applied? 
+  % MRS: though might be OK, since x^2 + y^2 = r^2 so maybe covariance are additive if x and y uncorrelated (which they should be)
 
@@
   dimensions as the equilibration time point.
+
+  \subsection{Generating Stochastic IHMM Trajectory Realizations}\label{method:realizations}
 
@@
 
-  \subsection{Parameter Clustering}\label{method:clustering}
+  \subsection{State Clustering}\label{method:clustering}
 
@@
 
-  %BJC: to be reworked after I have a working procedure.
+  \subsubsection*{Choosing the Number of Clusters}
+
   Choosing the number of clusters can be somewhat subjective so
@@
   test in order to score the quality of clustering as a function of the number 
-  of clusters chosen.~\cite{kaufman_finding_2009} For our data, the silhouette test generally favors the 
-  lowest number of clusters possible (see Section~\ref{S-section:nclusters} of
-  the Supporting Information). However, choosing too few clusters tends to 
-  not distinguish between visually obvious differences in 
-  dynamic behavior. This results in finalized parameter sets that are averages of
-  distinct behavior which presents further problems with the predictive modeling
-  that we discuss later on. We aimed to maintain the highest silhouette score,
-  and thus lowest number of clusters, possible while verifying that visually 
-  distinct states stayed separated. Based on these guidelines, we decided to 
-  group the $A$ and $\Sigma$ parameters into five clusters each and the radial
-  means into three clusters. Of the 75 distinct states allowed by this formulation,
-  the solutes in this study showed behavior from 32--36 distinct clusters. While
-  this may seem like a high number of states, many are sampled infrequently.
+  of clusters chosen.~\cite{kaufman_finding_2009} For our data, the silhouette 
+  test generally favors the lowest number of clusters possible (see 
+  Section~\ref{S-section:nclusters} of the Supporting Information). However, 
+  choosing too few clusters tends to not distinguish between visually obvious 
+  differences in dynamic behavior. This results in finalized parameter sets 
+  that are averages of distinct behavior which presents further problems with 
+  the predictive modeling that we discuss later on. We aimed to maintain the 
+  highest silhouette score, and thus lowest number of clusters, possible while
+  verifying that visually distinct states stayed separated.
+
+%  Based on these guidelines, we decided to 
+%  group the $A$ and $\Sigma$ parameters into five clusters each and the radial
+%  means into three clusters. Of the 75 distinct states allowed by this formulation,
+%  the solutes in this study showed behavior from 32--36 distinct clusters. While
+%  this may seem like a high number of states, many are sampled infrequently.
   %MRS: what is the consequence of being sampled infrequently.
+
+  \subsubsection*{Obtaining Parameters of Clustered States}
 
@@
   the clusters using the inference component of the IHMM algorithm. 
-%  generated a
-%  state transition probability matrix, $T$. The IHMM algorithm also produces an estimate
-%  of $T$, but since we fixed the state sequence, we decided to explicitly calculate $T$ 
-%  by counting the number of transitions between states compiled across all trajectories.
-%  We used the parameter inference component of the IHMM algorithm in order to 
-%  infer $A$ and $\Sigma$ of the clustered states.
-%  We could not simply take the mean of the clustered $A$ and $\mathbf{e}_t$ 
-%  parameters because it is not clear that this is a linear 
-%  operation for this problem. To circumvent this problem, 
   First, we modified the ($r$, $z$) solute trajectories so that they had a mean of zero,
@@
 
-  %BJC:This next paragraph can probably be moved
-%  Finally, we generated stochastic trajectory realizations using the clustered
-%  parameter sets. We drew state sequences with transition probabilities given by
-%  $T$. While in a given state, we simulated motion according to the VAR(1)
-%  parameterization of that state. After each state transition, we reset the 
-%  unconditional mean of each state based on the particle's position immediately
-%  before the state transition occurred.
-
-  %MRS: maybe ``using the parameterized model to explore mechanisms''
-  \subsection{Tools for Exploring Mechanisms}\label{method:interactions}
+  \subsection{Tools for using the Parameterized Model to Explore Mechanisms}\label{method:interactions}
 
@@
 
-  % BJC: It probably makes sense to put the trajectory generation and MSD predictions
-  % first since it will be part of how we justify our clustering choices.
+  \subsection{Automatic Detection of Distinct Dynamical Modes}\label{section:find_modes}
+
+  We applied the IHMM independently to all 24 trajectories of each of the four solutes studied.
+  \begin{itemize}
+    \item The number of states found for each trajectory varied between 5 and 30  %BJC2: need to see what these numbers actually are.
+    \item In Figure~\ref{fig:rz_unclustered}, we show the state sequence determined by the
+    IHMM for an example methanol trajectory.
+    \item The model distinguished many of the states due to differences in their mean levels 
+    while their fluctuations about those means are often similar. 
+    \item In Section~\ref{section:mechanisms}, we use clustering to reduce the total state
+    space for each solute.    
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{rz_unclustered_MET.pdf}
+  \caption{The IHMM found 24 distinct VAR(1) states in this representative methanol trajectory.}\label{fig:rz_unclustered}
+  \end{figure}
+
+  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}
+
+  % MRS: maybe makes sense to talk a little about what features/parameters of the 
+  % models the MSD is sensitive to?
+
+  Before analyzing solute behavior characteristic to the states identified by the
+  IHMM, it is important to verify whether the state dynamics are consistent with MD
+  both qualitatively and quantitatively.
+  \begin{itemize}
+    \item Therefore, we generated stochastic realizations based on the parameters 
+    of each trajectory as described in Section~\ref{method:realizations}.
+  \end{itemize}
+
+  As shown in Figure~\ref{fig:qualitative_unclustered}, realizations of our model 
+  can produce trajectories that show qualitatively similar hopping and trapping 
+  behavior to the MD trajectories.
+  \begin{itemize}
+    \item It is important that our model reproduces this behavior so that we can
+    have confidence in its usefulness for quantitative predictions.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{qualitative_unclustered_MET2.pdf}
+  \caption{We can generate trajectories which bear qualitative resemblance to
+  the MD trajectories. Solute trajectories generated by the IHMM (blue) show
+  the same hopping and trapping behavior exhibited by MD (black).
+  }\label{fig:qualitative_unclustered}
+  \end{figure}
+
+  \noindent From a quantitative standpoint, the model has two shortcomings.
+  \begin{itemize}
+  	\item First, in many cases, the MSD predicted by realizations of the IHMM 
+  	under-predicts that of MD (see Figure~\ref{fig:unclustered_msds}).
+  	\item Second, the shapes of the MSD curves at short time lags are very different.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{unclustered_msd_MET.pdf}
+  \caption{methanol}\label{fig:unclustered_msd_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{unclustered_msd_GCL.pdf}
+  \caption{ethylene glycol}\label{fig:unclustered_msd_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{unclustered_msd_URE.pdf}
+  \caption{urea}\label{fig:unclustered_msd_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{unclustered_msd_ACH.pdf}
+  \caption{acetic acid}\label{fig:unclustered_msd_ACH}
+  \end{subfigure}
+  \caption{The MD MSDs (black) of methanol and urea are under-predicted by 
+  the IHMM (orange), while the predictions match within uncertainty for ethylene
+  glycol and urea.}\label{fig:unclustered_msds}
+  \end{figure}
+
+  \noindent The IHMM under-predicts MD MSD due to its tendency to favor fewer states.\cite{}
+  \begin{itemize}
+    \item Disjoint segments with similar VAR parameters, but different lengths of 
+    entrapment can be parameterized as the same state.
+    \item In Figure~\ref{fig:dwell_distributions}, we compare the overall dwell 
+    time distributions generated directly from MD simulations to that generated from 
+    realizations of the IHMM. 
+    \item Some of the probability density of short trapping times in the MD simulations
+    gets shifted to medium length trapping times in realizations of the IHMM.
+    \item In Figure~\ref{fig:dwell_distributions_modT} and~\ref{fig:msd_modT}, we show 
+    that by modifying the transition matrix to encourage transitions towards states with
+    shorter dwell times, we can more closely reproduce the dwell time distribution and 
+    MSD of MD.
+    \item This is because most solute motion is a consequence of transitions between 
+    trapped states.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{dwell_distributions.pdf}
+  \caption{}\label{fig:dwell_distributions}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{dwell_distributions_modT.pdf}
+  \caption{}\label{fig:dwell_distributions_modT}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{unclustered_msd_MET_modT.pdf}
+  \caption{}\label{fig:msd_modT}
+  \end{subfigure}
+  \caption{(a) The density of short dwell times compiled from realizations of
+  the IHMM is below that measured directly from the MD trajectories. If we
+  modify the transition matrix in order to favor transitions towards states with
+  short dwell times, we can more closely match the (b) dwell time distributions
+  and (c) MSDs.}\label{fig:slow_T}
+  \end{figure}
+
+  At extremely short time lags, the MSD is generally over-predicted by the IHMM,
+  see Figure~\ref{fig:unclustered_msd_shortlag}, because the VAR(1) model assumes
+  multivariate Gaussian noise while the MD data suggests the noise is better 
+  modeled by more general L\'evy stable noise.
+  \begin{itemize}
+    \item The first time lag of the MSD is effectively the variance of all 
+    observed fluctuations. 
+    \item The IHMM simulation appears to over-estimate the variance because the 
+    actual distribution of hops has heavy tails with a smaller variance. (Figure~\ref{fig:emission_widths}).
+    \item The total distribution of hops is expected to be heavy tailed because
+    it is a combination of hop distributions from many state with different variances. 
+    \item More interestingly, in Figure ~\ref{fig:state_emission_widths}, we show that
+    the emission distribution of a single state picked out by the IHMM is fit better by
+    a more general L\'evy distribution while the emissions from IHMM realizations are
+    Gaussian, as expected.
+    \item An improvement to the IHMM that may allow dynamics more faithful to MD would
+    using an autoregressive model with L\'evy stable noise. However this would be 
+    less computationally efficient to lack of conjugate priors.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{unclustered_msd_MET_shortlag.pdf}
+  \caption{}\label{fig:unclustered_msd_shortlag}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{emission_widths.pdf}
+  \caption{}\label{fig:emission_widths}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{state_emission_widths.pdf}
+  \caption{}\label{fig:state_emission_widths}
+  \end{subfigure}
+  \caption{(a) At short time lags, the MD MSD (black) and the IHMM MSD (orange)
+  differ significantly in their shape and curvature. (b) While the 
+  fluctuations in $z$ of both distributions are heavy-tailed, fitting well to L\'evy
+  stable distributions, the IHMM has a wider variance. (c) The distribution of 
+  fluctuations in a state frequently visited by methanol is heavy tailed, but the 
+  IHMM is constrained to producing fluctuations from a Gaussian distribution ($\alpha$=2).
+  }\label{fig:short_timelags}
+  \end{figure}
+
+  Also apparent from Figure~\ref{fig:unclustered_msd_MET_shortlag} is that the 
+  curvature of the MD MSD is far more gradual than that generated by the IHMM.
+  \begin{itemize}
+    \item This is because the VAR(1) model is only correlated to its previous
+    fluctuation while the MD simulations suggest that correlation persists for
+    at least tens of nanoseconds.
+    % BJC2: could probably use a correlation function to suggest the AR order and stick the plot in SI
+    \item One may be able to reproduce the curvature at short time lags with
+    higher order VAR models, but it becomes a much more difficult parameterization
+    that would require significantly more data.
+    \item Since we are interested in longer time scale behavior, it is not an 
+    issue of great concern.
+  \end{itemize}
+
+  % BJC2: I'm not sure if the width of the hop length distribution has a significant 
+  % effect on average MSD, since it's symmetric. Something to test next week.
+
+  \subsection{Using IHMM Parameters to Predict Selectivity}\label{section:macroscopic_properties}
+
+  % BJC2: I think it makes sense to talk about selectivity here, but I'm not sure 
+  % the best way to go about it.
+
+  Keeping in mind the the shortcomings of the IHMM, we can now propagate realizations onto long 
+  time scales in order to predict solute flux and thus selectivity. 
+  \begin{itemize}
+    \item In our previous work, we showed that in systems without convective flux, selectivity is
+    simply the ratio of solute fluxes.
+%    \item Although the magnitude of our MSD predictions are typically below those of
+%    MD, we may still obtain reasonable estimates of selectivity.
+  \end{itemize}
+
+  The ratio of solute fluxes are sufficient to justify
+
+  \subsection{Learning Mechanisms from the IHMM}\label{section:mechanisms}
 
@@
   behavior exhibited by solutes over long MD trajectories in terms of 
-  solute-membrane interactions. In addition, we can use the IHMM in order to generate
-  stochastic trajectories, with dynamics similar to MD, so that we can estimate 
-  macroscopic transport properties. 	
-  %MRS: subsection lettering is really big - makes it seem like a very different section?
-
-  \subsection{Automatic Detection of Distinct Dynamical Modes}\label{section:find_modes}
-
-  We applied the IHMM to all trajectories of each of the four solutes studied.
-  Based on our choice of clustering, we identified over 30 distinct dynamical
-  modes for each solute. Many of these modes are sampled very infrequently and thus
-  do not contribute significantly to a general understanding of solute transport behavior.
-  In this section, we explore a subset of this data, focusing on the states
-  and dominant interactions most common to solute trajectories.
-
-  %MRS: maybe phrase it around types of mechanism, and use methanol as an example.
-  \subsubsection*{The Dynamics of Methanol}
-
-  Methanol exhibits a range of dynamic behavior. In Figure~\ref{fig:mechanism_map}, we
-  plot a representative 2D methanol trajectory in cylindrical coordinates. The coordinates
-  are colored according to the cluster with which methanol's dynamics are most consistent,
-  which implies that this particular methanol trajectory exhibits eight distinct dynamical 
-  behaviors (in order of their first appearance, they are colored dark yellow, red, light
-  blue, light green, orange, blue, teal and lime green). The solute time series are coupled
-  with color coded bars which describe the solute's local environment and physical 
-  interactions that it undergoes at that trajectory frame. From the top, they describe 
-  whether the solute is associated with sodium, whether the solute is hydrogen bonding
-  with the monomer as well as to what part of the monomer it is hydrogen bonding, and 
-  finally, the local number density surrounding the solute.
-
+  solute-membrane interactions.
+
+  \subsubsection*{State Clustering}
+
+  In order to reduce the state space to a more manageable size, and to allow
+  different solute trajectories to share similar behavior, we clustered the
+  states identified by the IHMM for each solute as described in 
+  Section~\ref{method:clustering}.
+  \begin{itemize}
+    \item In Figure~\ref{fig:mechanism_map}, we show the results of clustering on the same trajectory
+    from Figure~\ref{fig:rz_unclustered}.
+    \item We chose to use X clusters based on the criteria described in 
+    Section~\ref{method:clustering}.  %BJC2: might be some variation between solutes.
+    % BJC2: There will be figures in supporting to help justify number of clusters, but I don't want
+    % to dwell on it at all in the main text.
+    \item Therefore, we reduced the total state space from 300 to X.  %BJC: obviously these numbers will be updated
+    \item By working to understand the parameters of each cluster, we can 
+    gain an understanding of associated solute transport mechanisms responsible for 
+    those parameters.
+  \end{itemize}
+
+%  Using the parameters of the clustered states to generate stochastic realizations
+%  allows us to create representative trajectories which incorporate dynamics of
+%  all 24 solute trajectories.
+%  \begin{itemize}
+%    \item MSD under-predicted compared to unclustered states
+%  \end{itemize}
+
+  \subsubsection*{Relating Clusters to Mechanisms}
+  %The Dynamics of Methanol}
+
+  The parameters of each cluster can be related to dominant solute-membrane interactions.
+  \begin{itemize}
+    \item Based on our previous work, we know that hydrogen bonding, sodium ion 
+    association and radial location within the membrane pores will have a significant
+    influence on transport properties. 
+    \item Even without our previous work, it would still be easy to speculate that these 
+    interactions might occur and could therefore be used to help understand the 
+    states identified by the IHMM.
+    \item We have also incorporated membrane density as a physical metric because we 
+    know the membrane has an inhomogeneous structure.
+  \end{itemize}
+
+  In Figure~\ref{fig:mechanism_map}, we demonstrate the wide range of behavior exhibited
+  by a representative 2D methanol trajectory.
+%BJC2: reducing duplication
+%  The coordinates
+%  are colored according to the cluster with which methanol's dynamics are most consistent,
+%  which implies that this particular methanol trajectory exhibits eight distinct dynamical 
+%  behaviors (in order of their first appearance, they are colored dark yellow, red, light
+%  blue, light green, orange, blue, teal and lime green).
+  The solute time series are coupled with color coded bars which describe the solute's
+  local environment and physical interactions that it undergoes at each trajectory frame. 
+%  From the top, they describe 
+%  whether the solute is associated with sodium, whether the solute is hydrogen bonding
+%  with the monomer as well as to what part of the monomer it is hydrogen bonding, and 
+%  finally, the local number density surrounding the solute.
+
+  %BJC2: the exact figure will change, but most of what I say shouldn't
   \begin{figure}
@@
   %MRS: a lot of this caption test is duplicated from the main text. I would suggest reducing the duplication.
+  %BJC: you think better to have more detail in text or in caption?
   \caption{(a) We can learn a significant amount of detail about solute motion by viewing 
@@
 
-  %BJC: I'm not sure whether to spell out the numbers or not. 'six state' versus '6 states'; 'eight out of 24' or '8 out of 24'
-  % 'State one or State 1' 
+  % BJC2: the numbers and choices of states in this paragraph will change, but I think we
+  % can still use this framework to study mechanisms.
   We may learn the most by studying the dynamical modes common to the majority of 
@@
 
+  %BJC2: Again, this will change, but will follow the same general flow
   We can begin to dissect the dynamics of each state by studying their parameters.
@@
   mean. One could argue that the parameters of states 3--7 are actually very close which
-  suggests that solutes might behave alike in 
-  %MRS: changed word.
-  %topologically 
-  morphologically
-  distinct regions of the 
+  suggests that solutes might behave alike in morphologically distinct regions of the 
   membrane.
@@
   surprisingly, both states 3 and 5 correspond to solutes located close to a pore center,
-  where one might expect solute motion to be less restricted. 
-  %MRS: are thsse h-bonding states?
-  Although solutes in states
+  where one might expect solute motion to be less restricted. Although solutes in states
   4 and 6 are in the viscous tail region, their dwell times are only intermediate. This
@@
   \begin{subfigure}{0.35\textwidth}
-  % BJC: I'll bootstrap some error bars on this by drawing the transition probabilities 
-  % from a Dirichlet distribution.
   \includegraphics[width=\textwidth]{A_sigma_scatter_MET.pdf}
   \caption{}\label{fig:A_sigma_scatter_MET}
-  \includegraphics[width=\textwidth]{dwell_times_MET.pdf}  %BJC5: maybe better as 95 % confidence rather than mean
+  \includegraphics[width=\textwidth]{dwell_times_MET.pdf}  % No errorbars because these are expected values
   \caption{}\label{fig:dwell_times_MET}
@@
   %MRS: a lot of text here in the caption - think about reducing duplication with the text, and moving some to the text.
+  %BJC2: will rework once final plots are made.
   \caption{We can learn the most about methanol's behavior by studying the dynamics
@@
   The $y$-axis labels of the $r$ coordinate plot specify the radial mean of each clustered 
-  state. 
-  %MRS7: it's confusing to have the R not in order of r. Emphasize this more in the caption, 
-  %maybe think of something a bit different for the final paper. Reads odd to have numbers not in order along an axis.
-  %BJC7: indeed
-  The percentage of trajectories in which the states appear are labeled to the right of
+  state. The percentage of trajectories in which the states appear are labeled to the right of
   the $r$ plots. States 1--5 appear in the trajectory shown in Figure~\ref{fig:mechanism_map}
@@
 
+  %BJC2: A lot of the following will probably be reworked with different clustering scheme
   The types of hydrogen bonding undergone by solutes is dependent on radial
@@
 
-  % BJC5: I think I want to do an abbreviated study here on acetic acid or urea 
-  % since it will incorporate sodium ion association.
-
-  \subsubsection*{Behavior of Other Solutes}
-
-  We applied the IHMM to the other three solutes in this study: urea, acetic acid
+  \subsubsection*{Comparison of Solute Behavior}
+  %BJC2: Again, most of this section will get a facelift, but will try to follow same flow 
+  We applied similar analysis to the other three solutes in this study: urea, acetic acid
   and ethylene glycol. Not only can we use the model to study the dynamics of each 
@@
 
-%BJC: will move this earlier
-  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}
-
-  %MRS: maybe makes sense to talk a little about what features/parameters of the models the MSD is sensitive to?
-  %BJC5: something we can do for the supporting information to show that this approach is valid: Eliminate nonidealities in our MD trajectories (compared to a pure VAR process) and use toy data to generate trajectories based on some number of states with different parameters.
-Generate an MSD with those.
-See if we can reproduce with our model.
-Can also use this to test new strategies.
-  %MRS6: toy data is actually a VERY good idea.  Use a VAR process that looks like MD, and then try to cluster it, and figure out why different.
-
-  We can use the IHMM in order to generate stochastic trajectory realizations
-  which bear some qualitatively similar characteristics to those output
-  by our MD simulations. Because we clustered the data, we are left with a 
-  single transition probability matrix which allows transitions between dynamical
-  behaviors shared by the 24 MD trajectories. In 
-  Figure~\ref{fig:trajectory_realizations_MET}, we show some stochastic realizations
-  generated by our models compared directly to MD. The trajectories show clear 
-  periods of entrapment with intermittent hops.
-
-  %BJC5: the goal is to figure out how to fix this for the paper.
-  %BJC5: this is more of a 'how can this be improved' section for the dissertation.
-  %MRS6: got it.
-  The MD trajectories show much broader variability in their overall motion than realizations
-  of the IHMM model. 
-  %MRS6: definitely an important point for the paper: clustering things together might make trajectories too typical.
-  Some trajectories span a wide range of $z$ coordinates, while others stay
-  trapped for nearly the entire simulation. Our model is very unlikely to generate 
-  trajectories with dwell times similar to the third MD trajectory shown in 
-  Figure~\ref{fig:trajectory_realizations_MET}. This is because the realizations 
-  generated by our model are representative of the average behavior of solutes studied.
-  It is possible that certain states with long dwell times should have been
-  clustered as their own, but the transition probabilities would have high uncertainties.
-        %MRS6: is it necessarily a problem that the transition probabilities have high uncertainties?
-If one is drawing from the Dirichlet distribution, uncertainty isn't a big deal.
-The trapping just doesn't quite seem to be as long as MD.
-        %MRS6: the other issue is apparent suppression on variance in the jumps, but that may be harder to get. 
-  It is also possible that we should not be using a static transition matrix in 
-  order to generate stochastic trajectories, but rather sample the rows of the transition
-  matrix from a Dirichlet distribution since average dwell times are highly sensitive to
-  self transition probabilities.
-        %MRS6: right uncertainty matters less here.
-  %BJC5: maybe a figure showing the MSDs of all the MD trajectories versus a subset of 
-  % stochastically generated trajectories. I image the stochastic ones will have a much
-  % tighter distribution.
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{trajectory_realizations_MET.pdf}
-  \caption{We can generate trajectories which bear some qualitative resemblance to the MD 
-  trajectories. Solute trajectories generated by our model (blue) show the same
-  hopping and trapping behavior exhibited by MD (black). The behavior of individual 
-  MD trajectories tend to show wider variability than our model's realization because
-  the model effectively represents the average behavior of the MD trajectories. This 
-  implies that much longer simulations or a different method of trajectory generation might
-  be necessary in order to obtain stochastic realizations with the same range of behavior
-  as MD.
-  }\label{fig:trajectory_realizations_MET}
-  \end{figure}
-
-  The MSDs calculated by stochastic realizations of our model are quantitatively similar to
-  MD. For all solutes except acetic acid, our predicted MSD curves lie close to but below the
-  1$\sigma$ confidence intervals of MD. However, in these cases, the average MD MSDs are 
-  driven up by single trajectories with uncharacteristically large MSDs. It is possible that
-  an improved trajectory generation approach may allow for this highly variable behavior.
-  If we remove these uncharacteristic trajectories, the agreement between MD and our realizations
-  improves. Acetic acid has no obvious outliers and shows good agreement between MD and
-  IHMM realizations.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{msd_MET.pdf}
-  \caption{}\label{fig:msd_MET}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{msd_GCL.pdf}
-  \caption{}\label{fig:msd_GCL}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{msd_URE.pdf}
-  \caption{}\label{fig:msd_URE}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{msd_ACH.pdf}
-  \caption{}\label{fig:msd_ACH}
-  \end{subfigure}
-  \caption{The MSDs predicted based on 1000 realizations of our model (blue) tend to underpredict
-  the MSDs based on the MD trajectories (black). Due to the variability in solute behavior across MD trajectories,
-  as demonstrated in Figure~\ref{fig:trajectory_realizations_MET}, there are several 
-  individual solute MSD curves that are significantly higher than the rest and drive up the
-  mean of the MSD. If we remove those trajectories from the MSD calculation, we obtain 
-  estimates much closer to the IHMM estimate.(I haven't done it yet, but could plot a third curve
-  with outlier removed). Acetic acid, has no obvious outliers which is consistent with our model's
-  prediction which lies within the 1$\sigma$ confidence interval of MD after a 1000 ns time lag.}\label{fig:msds}
-  \end{figure}
-
-  % BJC3: maybe need to talk about the curvature. Our model shouldn't have noticeable
-  % curvature because it's only correlated with one step
-
   \section{Conclusion}

### 2020-05-09 Ben_Manuscripts/hdphmm/Draft.tex
Comments on draft.

@@
   solute-membrane interactions.
-% order to automatically detect and parameterize an unknown number of
-%  latent vector autoregressive dynamical modes. 
-  %MRS: in above sentence: try to rephrase around the physical information obtained (mechanism or properties) rather than the mathematical route to it.
-  %BJC2: gave a try
-
-  %MRS: below - it's not the solute behavior, though, it's states identified by them model. Rephrase?
-  %BJC2: I think this is better?
+
   We group the states identified by the IHMM into clusters based on multiple metrics
@@
   prevalent clusters in order to relate their parameters to physical interactions between 
-  solutes and the membrane. This enhancement to our understanding of the diverse range 
-  of influential solute-membrane interactions allows us to hypothesize design changes 
-  to LLC monomers aimed towards controlling the rates of solute passage, thus improving 
-  the selective performance of LLC membranes.
+  solutes and the membrane.
 
@@
   Overall, this work provides an effective way to simultaneously identify transport 
-  mechanisms in 
-  %BJC2: porous nanoscale to nanoporous? 
-  %porous nanoscale 
-  nanoporous materials and project complex diffusive behavior on
-  long time scales.
+  mechanisms in  nanoporous materials and project complex diffusive behavior on
+  long time scales.  This enhancement to our understanding of the diverse range 
+  of solute behavior allows us to hypothesize design changes 
+  to LLC monomers aimed towards controlling the rates of solute passage, thus improving 
+  the selective performance of LLC membranes.
 
@@
   	time scales accessible to MD simulation, one cannot calculate reliable diffusion 
-  	constants since solute mean square displacements (MSDs) are non-linear.
+  	constants since solute mean square displacements (MSDs) are non-linear 
+        %MRS2: added
+        on timescales accessible to molecular simulation.
   	\item Therefore, we are in need of a more flexible approach for modeling solute 
@@
     in single particle trajectory analysis.
-    %MRS: Then say it hasn't been used in this context (do we know of any, if not say so).
+    %MRS: Then say it hasn't been used in this context (do we know of any, then cite, if none we have found, say so.)
     \item The IHMM has not been used much for MD trajectory analysis.
@@
   correspond to the center of mass coordinates of the solutes versus time, and the
-  states correspond to the dynamical behavior which give rise to those types
+  states correspond to 
+  % MRS2: added - ``states'' aren't quite ``behavior''
+  segments of the trajectory with similar
+  dynamical behavior which gives rise to those types
   of observations. The probability of transitioning to a state based on the current
-  state is mathematically defined in terms of an $n\times n$ transition probability
+  state is 
+  %MRS2: redundant
+  % mathematically 
+  defined in terms of an $n\times n$ transition probability
   matrix, $T$, where $n$ is the number of states. Unfortunately, standard HMMs 
@@
   % a reproduction of Fox et al's explanation: https://ieeexplore.ieee.org/abstract/document/5563110
+  %MRS2: this is fine.
   The infinite-state HMM overcomes this drawback by placing a hierarchical
@@
   parameters for each state and the overall state transition probability matrix, $T$.
-  We created a python implementation of this process which we heavily adapted from
+  We created a Python implementation of this process which we heavily adapted from
   the MATLAB code of Fox et al.~\cite{fox_bayesian_2010} Parameter estimation is iterative. 
+  %MRS2: give location for the code here where you introduce it.
   Therefore, we looked for convergence of the parameters in Equation~\ref{eqn:var}.
@@
   % MRS: though might be OK, since x^2 + y^2 = r^2 so maybe covariance are additive if x and y uncorrelated (which they should be)
-
+  % MRS2: As I mentioned before, the issue is if the likelihood for the covariance matrix is properly defined for radial diffusion.
+We can check over the equations.
+It likely wouldn't change the qualitative results much, but should ne checked.
+Would not affect the clustering.
   We defined the final parameters of each state as the mean of the parameters 
@@
 
-  %MRS: maybe add subsubsections naming/labeling each part of the process so that people have a sense of the steps,
-  %MRS: makes it easier to read.
+  %MRS2: maybe add subsubsections naming/labeling each part of the process so that people have a sense of the steps,
+  %MRS2: makes it easier to read.
   We clustered like parameter sets in order to reduce the state space to
@@
   and the self-transition probabilities, $T_{ii}$, of each state for a total of 6 clustering
-  dimensions. The means in $r$ are likely meaningful since the membrane is inhomogeneous, 
-  transitioning from hydrophilic pores to hydrophobic tails. To cluster on $T_{ii}$, we first
+  dimensions. The means in $r$ are likely meaningful since the membrane is 
+  %MRS2: added
+  radially inhomogeneous from each pore, 
+  transitioning from hydrophilic pores to hydrophobic tails. 
+  %MRS2: 
+  However, the channels are isotropic in $z$ so we do not cluster on $\mu_z$.
+  To cluster on $T_{ii}$, we first
   cast it in terms of the expected dwell times. The expected value of the number of sequential
@@
   Since our system is in a monoclinic unit cell, we periodically replicated
-  the system in the +/- x, y and z directions and then chose the bounds on the
+  the system in the $\pm$$x$, $y$ and $z$ directions and then chose the bounds on the
   histogram in order to create a rectangular box encompassing the unit cell with
@@
   \end{equation}
-  where T is the length of the trajectory. We reported 1$\sigma$ confidence intervals 
+  where T is the length of the trajectory. We reported $1 \sigma$ confidence intervals 
   based on the results of 200 bootstrap trials. For each trail, we calculated the mean of 
@@
   glycol and urea.}\label{fig:unclustered_msds}
+  %MRS2: to save space, could consider the graphs in 1x4 across the top, with a single legend (since all have the same), and slightly thicker lines  %There are only 2 lines per plot, so it's not too noisy to be that size
   \end{figure}
 
+  %MRS2: I'd make this a separate subsection ``Deviations of the IMMM from molecular motion'' or something like that.
   \noindent The IHMM under-predicts MD MSD due to its tendency to favor fewer states.\cite{}
@@
 
+  %MRS2: reference not working?
   Also apparent from Figure~\ref{fig:unclustered_msd_MET_shortlag} is that the 
@@
   %BJC: you think better to have more detail in text or in caption?
+  %MRS2: at a certain point, it should be in the text.  In the caption, I would just state what the point of the plot is, 
+  % and define the colors/data/etc.  But full explanation would be better in the text. Captions should be scannable quickly,
+  % based on how people process papers, and this should be significantly shorter for readability. 
  \caption{(a) We can learn a significant amount of detail about solute motion by viewing 
@@
 
+  %MRS2: suggest subsubcaptions/italics at the start of parentheses to make it easier for a reader to see the structure.
+  %MRS2: like \textit{hydrogen bonding patterns}: etc.
+
   One can gain useful chemical intuition just by studying plots like
@@
 
+  %MRS2: not entirely clear about the purpose of this paragraph? Seems to be just saying it's possible to learn more?
+  %MRS2: should clarify.
   It is clear that there is a wealth of information in these plots, but they don't give
@@
   to all other states. This should lead to significant solute displacement. Covariance in each dimension
-  appears to have a strong correlation. States 3--6 all have relatively low covariances, which may
+  appears to have a strong correlation. 
+  %MRS2: correlation with what?
+  States 3--6 all have relatively low covariances, which may
   be characteristic of trapped states. They are primarily distinguished based on the magnitude of their 
@@
   We also show the solute MSDs after a 1000 ns time lag. It is not immediately obvious
-  why the MSDs follow this trend. The states identified by the IHMM shed
+  why the MSDs follow this trend. 
+  %MRS2: be more precise what ``this trend'' is.
+  The states identified by the IHMM shed
   some light on the reasoning.

### 2020-05-10 Ben_Manuscripts/hdphmm/Draft.tex
Updates to methods and clustering

@@
 
-  % MRS: going to JPC, so emphasize the physical systems.
   There is a need for highly selective membranes in order to perform efficient 
@@
   fluctuations with macroscopic observables.
-  %MRS: should explicitly point out that just calculating diffusion coefficients don't work for subdiffusive behavior, so
-  %MRS need a different way to do it.
-  %BJC2: added last two bullet points
   \begin{itemize}
@@
   	\item In many systems, it's possible to achieve this by calculating diffusion 
-  	constants.\cite{}
-  	\item Unfortunately, for systems which exhibit complex subdiffusive dynamics on the
-  	time scales accessible to MD simulation, one cannot calculate reliable diffusion 
+  	constants.%\cite{}
+  	\item Unfortunately, for systems which exhibit complex short timescale 
+  	subdiffusive dynamics, one cannot calculate reliable diffusion 
   	constants since solute mean square displacements (MSDs) are non-linear 
-        %MRS2: added
-        on timescales accessible to molecular simulation.
+    on the timescales accessible to molecular simulation.
   	\item Therefore, we are in need of a more flexible approach for modeling solute 
   	dynamics which makes less assumptions about the solute's average behavior.
-  	%BJC2: I'm moving these towards the end
-%  	\item There are two main challenges associated with this goal.
-%  	%since complex and
-%  	%diverse diffusive motion on time scales accessible to molecular simulations prevents
-%  	%us from easily relating chemically dependent solute motion to experimental time scales.
-%  	\item First, we need a simple way to identify and parameterize the fluctuations
-%  	characteristic to dominant solute-membrane interactions.
-%  	\item Second, we need a way to propagate this behavior far beyond the time scales
-%  	afforded by MD.
-  \end{itemize}
-
-  %MRS: point out that LLC's are examples where there are lots of hopping/jumping (cite previous papers) and
-  %MRS: so we need different approaches.
-  %BJC2: added last bullet point to lead in to following paragraph
+  \end{itemize}
+
   In this work, we are particularly interested in the design of lyotropic liquid crystal (LLC)
@@
 	design with measurable quantities.
-	\item This goal is complicated by the non-Brownian hopping and trapping behavior
-	induced by the membrane's diverse topology and inhomogeneous structure.~\cite{coscia_understanding_2019,coscia_chemically_2019}
+	\item This goal is complicated by the non-Brownian hopping and trapping behavior induced
+	by the membrane's diverse topology and inhomogeneous structure.~\cite{coscia_understanding_2019,coscia_chemically_2019}
   \end{itemize}
@@
     \item It's been used extensively for speaker diarization and has found some application
-    in single particle trajectory analysis.
+    in single particle trajectory analysis.~\cite{calderon_inferring_2015,fox_sticky_2011}
     %MRS: Then say it hasn't been used in this context (do we know of any, then cite, if none we have found, say so.)
@@
 
-  We aim to address two primary scientific 
-  questions with this work. 
-  First, we want
-  to know if the IHMM algorithm can help researchers efficiently uncover underlying
-  transport mechanisms which give rise to different solute dynamical behavior.
-  Second, we want to predict macroscopic transport by using our model to generate 
-  stochastic solute trajectories at much longer timescales than possible with MD simulations, 
-  extending into timescale where diffusive behavior again occurs.
-
+  We aim to address two primary scientific questions with this work:
+  First, we want to know whether it is possible to predict macroscopic transport
+  properties. We use the VAR parameters and state transition probability matrix of
+  the IHMM in order to generate stochastic trajectory realizations with behavior 
+  similar to that exhibited by MD. One can project these realizations onto much 
+  longer timescales with computational ease extending into timescales where 
+  regular diffusive behavior again occurs.
+  Second, we want to know if the IHMM algorithm can help researchers
+  efficiently uncover underlying transport mechanisms which give rise to different 
+  solute dynamical behavior.
   We use the parameters of the states identified by the IHMM in order to infer 
@@
   solute-membrane interactions.
-
-  Finally, we use the VAR parameters and state transition probability matrix in
-  order to generate stochastic trajectory realizations with behavior similar to that
-  exhibited by MD. 
-  \begin{itemize}  
-    \item One can project these realizations onto much longer timescales with 
-    computational ease and use them to predict macroscopic properties.
-  \end{itemize}
 
@@
   correspond to the center of mass coordinates of the solutes versus time, and the
-  states correspond to 
-  % MRS2: added - ``states'' aren't quite ``behavior''
-  segments of the trajectory with similar
-  dynamical behavior which gives rise to those types
-  of observations. The probability of transitioning to a state based on the current
-  state is 
-  %MRS2: redundant
-  % mathematically 
-  defined in terms of an $n\times n$ transition probability
-  matrix, $T$, where $n$ is the number of states. Unfortunately, standard HMMs 
-  require $n$ to be known \textit{a priori}. One can partially overcome this by 
-  testing a range of numbers of hidden states and determining which is the best 
-  representation of the data.~\cite{pohle_selecting_2017}
-
-  %BJC: I'm not sure how much of this I should include. This is pretty much 
-  % a reproduction of Fox et al's explanation: https://ieeexplore.ieee.org/abstract/document/5563110
-  %MRS2: this is fine.
+  states correspond to segments of the trajectory with similar dynamical behavior 
+  which gives rise to those types of observations. The probability of transitioning 
+  to a state based on the current state is defined in terms of an $n\times n$ 
+  transition probability matrix, $T$, where $n$ is the number of states. Unfortunately,
+  standard HMMs require $n$ to be known \textit{a priori}. One can partially overcome
+  this by testing a range of numbers of hidden states and determining which is the
+  best representation of the data.~\cite{pohle_selecting_2017}
+
   The infinite-state HMM overcomes this drawback by placing a hierarchical
@@
   %MRS2: give location for the code here where you introduce it.
+  %BJC3: I emailed Emily Fox and she just asked me to use this citation. I'm happy to add a 
+  %link to where she stores the code. Would that be best in the form of a reference?
   Therefore, we looked for convergence of the parameters in Equation~\ref{eqn:var}.
-  % each entry in the $\mathbf{c}$ vector as well as the $A$ and $\Sigma$ matrices of Equation~\ref{eqn:var}. 
-  We detected equilibration 
-  of the parameters using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
+  We detected equilibration of the parameters using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
   on the time series of parameter estimates. Plots illustrating parameter convergence are 
@@
 
-  %BJC2: I say 'applied' a lot. Diversity that eventually
-  We carefully applied the IHMM algorithm in a way which takes advantage of the
-  system's cylindrical symmetry. While there
-  are a number of viable ways in which one could choose to analyze these time series,
-  we chose to use a multi-step procedure that we believe adequately distinguishes 
-  every type of distinct dynamical behavior exhibited by the solutes. The final
-  parameterization of the model is in cylindrical coordinates since each pore is a
-  cylinder where we expect solutes to exhibit radially symmetric dynamics. We 
-  present a step-by-step demonstration of the procedure that follows in 
-  Section~\ref{S-section:ihmm_procedure} of the Supporting Information.
+  % BJC3: Cut this paragraph
+%  We carefully applied the IHMM algorithm in a way which takes advantage of the
+%  system's cylindrical symmetry. While there are a number of viable ways in which
+%  one could choose to analyze these time series, we chose to use a multi-step 
+%  procedure that we believe adequately distinguishes the diversity of dynamical 
+%  behavior exhibited by the solutes. The final parameterization of the model is 
+%  in cylindrical coordinates since each pore is a cylinder where we expect 
+%  solutes to exhibit radially symmetric dynamics. We present a step-by-step 
+%  demonstration of the procedure that follows in 
+%  Section~\ref{S-section:ihmm_procedure} of the Supporting Information.
 
@@
   coordinates while estimating the state sequence.
-
-  We applied the IHMM to each of the 24 solute trajectories independently.
+  %BJC3: maybe could say something about multivariate guassian noise with VAR in cylindrical doesnt work with current code.
+
+  We parameterized each of the 24 solute trajectories independently.
   Although the IHMM is capable of identifying an infinite number of states, 
@@
   and $\Sigma$ parameters in segments with a relatively low number of emissions.
-  In these cases, plateauing of the mean in each dimension tends to be a more reliable indicator of
-  convergence (see Figure~\ref{S-fig:convergence3d} of the Supporting Information).
-
-  We reparameterized the time series, preserving the state sequence, in terms
-  of the radial and axial coordinates ($r$, $z$) due to the system's radial 
-  symmetry. We converted the $x$ and $y$ center-of-mass coordinates to $r$. 
-  We fixed the state sequence from the 3D parameterization and applied the 
-  inference component of the IHMM procedure to the cylindrical trajectories 
-  in order to estimate the VAR(1) parameters in terms of $r$ and $z$. Since
-  we fixed the state sequence, and we are using conjugate priors, the VAR 
-  parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}).
-  Therefore, we only ran the inference procedure for 100 iterations. 
-  % MRS: hmm. Here the new covariance parameters is redone in r - does there need to be any transformation applied? 
-  % MRS: though might be OK, since x^2 + y^2 = r^2 so maybe covariance are additive if x and y uncorrelated (which they should be)
-  % MRS2: As I mentioned before, the issue is if the likelihood for the covariance matrix is properly defined for radial diffusion.
+  In these cases, plateauing of the mean in each dimension tends to be a more 
+  reliable indicator of convergence (see Figure~\ref{S-fig:convergence3d} of
+  the Supporting Information).
+
+  % BJC3: This paragraph no longer necessary
+%  We reparameterized the time series, preserving the state sequence, in terms
+%  of the radial and axial coordinates ($r$, $z$) due to the system's radial 
+%  symmetry. We converted the $x$ and $y$ center-of-mass coordinates to $r$. 
+%  We fixed the state sequence from the 3D parameterization and applied the 
+%  inference component of the IHMM procedure to the cylindrical trajectories 
+%  in order to estimate the VAR(1) parameters in terms of $r$ and $z$. Since
+%  we fixed the state sequence, and we are using conjugate priors, the VAR 
+%  parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}).
+%  Therefore, we only ran the inference procedure for 100 iterations. 
+%  % MRS: hmm. Here the new covariance parameters is redone in r - does there need to be any transformation applied? 
+%  % MRS: though might be OK, since x^2 + y^2 = r^2 so maybe covariance are additive if x and y uncorrelated (which they should be)
+%  % MRS2: As I mentioned before, the issue is if the likelihood for the covariance matrix is properly defined for radial diffusion.
 We can check over the equations.
@@
 Would not affect the clustering.
-  We defined the final parameters of each state as the mean of the parameters 
-  from each iteration recorded after the equilibration time point. We found the 
-  equilibration time point of each component of the $\mathbf{c}$ vector as well as 
-  $A$ and $\Sigma$ matrices, and then used the longest equilibration time of all 
-  dimensions as the equilibration time point.
-
-  \subsection{Generating Stochastic IHMM Trajectory Realizations}\label{method:realizations}
-
-  %BJC: I'll need to expand on this a bit to make it clear. Talk about the bootstrapping etc.
-  Finally, we generated stochastic trajectory realizations using the finalized
-  parameter sets. We drew state sequences with transition probabilities given by
-  $T$. While in a given state, we simulated motion according to the VAR(1)
-  parameterization of that state. After each state transition, we reset the 
-  unconditional mean of each state based on the particle's position immediately
-  before the state transition occurred.
+%  We defined the final parameters of each state as the mean of the parameters 
+%  from each iteration recorded after the equilibration time point. We found the 
+%  equilibration time point of each component of the $\mathbf{c}$ vector as well as 
+%  $A$ and $\Sigma$ matrices, and then used the longest equilibration time of all 
+%  dimensions as the equilibration time point.
+
+  \subsubsection*{Predicting Mean Squared Displacement}\label{method:realizations}
+
+  %BJC3: expanded
+  \textit{Generating Stochastic IHMM Trajectory Realizations}: For each independent 
+  MD trajectory, we generated stochastic trajectory realizations using the finalized 
+  parameters of the associated IHMM. We drew state sequences with transition probabilities
+  given by $T$. While in a given state, we simulated motion according to the VAR(1) 
+  parameterization of that state. After each state transition, we set the unconditional
+  mean of the new state to the particle's position immediately before the state 
+  transition occurred.
+
+  %BJC3: this is new, not sure of clarity
+  \textit{Calculating MSD}: The MSD reported for each solute measured by our MD 
+  simulations is a distribution created from the 24 independent MSD curves. We predicted 
+  MSDs and their uncertainties with our stochastic models by bootstrapping the 
+  distribution of stochastically generated MSDs. For each bootstrap trial, we generated
+  24 independent trajectories using the 24 sets of IHMM parameters. We report the mean
+  and standard error of the bootstrapped MSD distributions.
 
@@
 
-  %MRS2: maybe add subsubsections naming/labeling each part of the process so that people have a sense of the steps,
-  %MRS2: makes it easier to read.
   We clustered like parameter sets in order to reduce the state space to
@@
   independent states, each with separate VAR(1) parameters. Many of these states
-  exhibit very similar dynamical behavior except their mean levels in $r$ and $z$
+  exhibit very similar dynamical behavior except their mean levels in each dimension
   are different.
@@
   tend to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
-  of the Supporting Information).
+  of the Supporting Information), which could cause the clustered model to combine 
+  distinct behavior into a non-existent hybrid state.
   %MRS: not clear what the consequence of the above is?
-
-  We clustered based on the eigenvalues of $A$ and $\Sigma$, the radial means, $\mu_r$, 
-  and the self-transition probabilities, $T_{ii}$, of each state for a total of 6 clustering
-  dimensions. The means in $r$ are likely meaningful since the membrane is 
-  %MRS2: added
-  radially inhomogeneous from each pore, 
-  transitioning from hydrophilic pores to hydrophobic tails. 
-  %MRS2: 
-  However, the channels are isotropic in $z$ so we do not cluster on $\mu_z$.
-  To cluster on $T_{ii}$, we first
-  cast it in terms of the expected dwell times. The expected value of the number of sequential
-  self-transitions is simply $\frac{1}{1 - T_{ii}}$. This relationship correctly implies that 
-  dwell times approach infinity as $T_{ii}$ approaches 1. There we found the most success with
-  agglomerative clustering by linearizing this relationship and clustering on $-\log(1 - T_{ii})$
-  (see Section\ref{S-section:selfT_cluster} of the Supporting Information for a graphical
-  illustration).
+  %BJC3: added a little to the end
+
+  %BJC3: reworked the following and split into paragraphs
+  We clustered based on the eigenvalues of $A$ and $\Sigma$, the distance from the 
+  pore center and the self-transition probabilities, $T_{ii}$, of each state. $A$ 
+  and $\Sigma$ capture the correlation and size of fluctuations. $T_{ii}$ is directly
+  related to the average time spent in each state. The distance from the closest pore 
+  center is likely meaningful since the membrane is radially inhomogeneous from each 
+  pore, transitioning from hydrophilic pores to hydrophobic tails. However, the 
+  channels are isotropic along the pore axis so we do not in means in the $z$ dimension.
+  We normalized each clustering dimension by its variance and shifted the mean to zero.
+
+  To take advantage of the system's cylindrical symmetry, we converted the parameters that
+  are directly related to solute position into cylindrical coordinates before clustering. We 
+  converted the $x$ and $y$ eigenvalues of $\Sigma$ and $A$ as $\lambda_x$ + $\lambda_y$
+  and $\lambda_x^2$ + $\lambda_y^2$ respectively. %BJC3: possibly could use some justification of these definitions. 
+  We obtained means in $r$, $\mu_r$, using the norm of the $x$ and $y$ means, 
+  $\sqrt{\mu_x^2 + \mu_y^2}$. We squared $\mu_r$ for clustering in order to cast it in the
+  same units as $A$ and $\Sigma$.
+
+  To cluster on $T_{ii}$, we first cast it in terms of the expected dwell times. The expected
+  value of the number of sequential self-transitions is simply $\frac{1}{1 - T_{ii}}$. This 
+  relationship correctly implies that dwell times approach infinity as $T_{ii}$ approaches
+  1. Therefore we found the most success with agglomerative clustering by linearizing this
+  relationship and clustering on $-\log(1 - T_{ii})$ (see Section~\ref{S-section:selfT_cluster}
+  of the Supporting Information for a graphical illustration).
 
@@
 
-%  Based on these guidelines, we decided to 
-%  group the $A$ and $\Sigma$ parameters into five clusters each and the radial
-%  means into three clusters. Of the 75 distinct states allowed by this formulation,
-%  the solutes in this study showed behavior from 32--36 distinct clusters. While
-%  this may seem like a high number of states, many are sampled infrequently.
-  %MRS: what is the consequence of being sampled infrequently.
-
   \subsubsection*{Obtaining Parameters of Clustered States}
 
-  We remapped the state sequence based on the cluster assignments and parameterized
-  the clusters using the inference component of the IHMM algorithm. 
-  First, we modified the ($r$, $z$) solute trajectories so that they had a mean of zero,
-  leaving only the fluctuations. We did this by subtracting the mean from each 
-  same-state segment of the unclustered trajectory. We used the IHMM algorithm on this
-  modified trajectory to infer the clustered state parameters by fixing the clustered 
-  state sequence.
+  %BJC3: modified
+  We remapped and fixed the state sequence based on the cluster assignments and
+  parameterized the clusters using the inference component of the IHMM algorithm. 
+  First, we modified the ($x$, $y$, $z$) solute trajectories so that they had a 
+  mean of zero, leaving only the fluctuations. First, we zeroed the $y$ component
+  of the trajectories by rotating the coordinates about the pore axis such that 
+  the mean vector of each separate segment was aligned with the $x$ axis. Next, 
+  we subtracted the means from each separate segment in the $x$ and $z$ dimensions.
+  We used the IHMM algorithm on this modified trajectory to infer the clustered 
+  state parameters by fixing the clustered state sequence.
 
   We obtained $\mathbf{c}$ vectors of the clustered states by averaging 
-  each value of $\mathbf{c}$ assigned to the same cluster. Note that we only care
-  about the $r$ component of $\mathbf{c}$ because solute trajectories are not 
-  bound in the $z$ direction.
+  each value of the rotated $\mathbf{c}$ vectors assigned to the same cluster. Note
+  that we only care about the $x$ and $y$ component of $\mathbf{c}$ because solute 
+  trajectories are not bound in the $z$ direction.
 
@@
   Since our system is in a monoclinic unit cell, we periodically replicated
-  the system in the $\pm$$x$, $y$ and $z$ directions and then chose the bounds on the
+  the system in the $\pm x$, $y$ and $z$ directions and then chose the bounds on the
   histogram in order to create a rectangular box encompassing the unit cell with
@@
   %MRS2: to save space, could consider the graphs in 1x4 across the top, with a single legend (since all have the same), and slightly thicker lines  %There are only 2 lines per plot, so it's not too noisy to be that size
+  %BJC3: good point
   \end{figure}
@@
   %MRS2: I'd make this a separate subsection ``Deviations of the IMMM from molecular motion'' or something like that.
-  \noindent The IHMM under-predicts MD MSD due to its tendency to favor fewer states.\cite{}
+  % BJC3: would these subsubsection headers look better as just italicized and on 
+  % the same line as where the next paragraph starts?
+  \subsubsection*{Deviations of the IHMM from Molecular Motion}
+
+  \noindent The IHMM under-predicts MD MSD due to its tendency to favor fewer states.%\cite{}
   \begin{itemize}
@@
 
-  %MRS2: reference not working?
-  Also apparent from Figure~\ref{fig:unclustered_msd_MET_shortlag} is that the 
+  Also apparent from Figure~\ref{fig:unclustered_msd_shortlag} is that the 
   curvature of the MD MSD is far more gradual than that generated by the IHMM.
@@
 
-  In Figure~\ref{fig:mechanism_map}, we demonstrate the wide range of behavior exhibited
-  by a representative 2D methanol trajectory.
+  \textit{Learning from individual trajectories}: In Figure~\ref{fig:mechanism_map}, 
+  we demonstrate the wide range of behavior exhibited by a representative 2D methanol
+  trajectory.
 %BJC2: reducing duplication
@@
   %MRS2: should clarify.
-  It is clear that there is a wealth of information in these plots, but they don't give
-  the complete picture needed in order to formulate LLC membrane design principles. One
-  can analyze each segment sequentially and form a clear picture of this instance of 
-  methanol's behavior without the need to visualize the trajectory with software like VMD.~\cite{humphrey_vmd:_1996}
-  However, it is still possible to gain a more general understanding of methanol's average
-  behavior.
+  %BJC3: It was meant to be transitory but can probably cut out with the addition of the subsection title
+%  It is clear that there is a wealth of information in these plots, but they don't give
+%  the complete picture needed in order to formulate LLC membrane design principles. One
+%  can analyze each segment sequentially and form a clear picture of this instance of 
+%  methanol's behavior without the need to visualize the trajectory with software like VMD.~\cite{humphrey_vmd:_1996}
+%  However, it is still possible to gain a more general understanding of methanol's average
+%  behavior.
 
@@
   % can still use this framework to study mechanisms.
-  We may learn the most by studying the dynamical modes common to the majority of 
+  \textit{Learning from all trajectories}: We may learn the most by studying the
+  dynamical modes common to the majority of 
   the solute trajectories. Using the IHMM, we identified 33 total dynamical modes 
@@
 
-  Most of what we have learned thus far has been based on the parameters of our
-  model with some qualitative validation using a single methanol trajectory. While 
+  \textit{Relating Parameters to Solute-Membrane Interactions}: Most of what we 
+  have learned thus far has been based on the parameters of our model with some 
+  qualitative validation using a single methanol trajectory. While 
   we may be able to further corroborate our arguments by analyzing more
@@
   %BJC2: A lot of the following will probably be reworked with different clustering scheme
+%  \textit{Hydrogen Bonding Patterns}: 
   The types of hydrogen bonding undergone by solutes is dependent on radial
@@
   groups and ether linkages. States with radial means greater than 1 nm (states 2,
-  4, 6 and 7) tend to hydrogen bond with the monomer tails. 
-  %MRS: tweak
-  %In the past we've 
-  Our previous work has
+  4, 6 and 7) tend to hydrogen bond with the monomer tails. Our previous work has
   shown that there is a gradual transition from the hydrophilic to hydrophobic region in

### 2020-05-10 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Updates to methods and clustering

@@
   	pore center (see Figure~\ref{fig:xyz_hmm}). 		
-  	\item Convert $x$ and $y$ coordinates to radial coordinates, $r$, then fix the state sequence
-  	and use the inference component of the IHMM in order to estimate the parameters in terms
-  	of $r$ and $z$ (see Figure~\ref{fig:rz_hmm}). 	 	
-  	\item Cluster the VAR parameters from the states found in all 24 trajectories. Reassign the state
-  	sequence so that segments which belong to the same cluster are labeled the same across all solute
-  	trajectories.
-  	\item Subtract the mean of each segment, obtained before clustering, in order to zero out the
-  	trajectory.
+  	\item Cluster the VAR parameters from the states found in all 24 trajectories (See 
+  	Section~\ref{method:clustering} of the main text). Reassign the state sequence so that segments
+  	which belong to the same cluster are labeled the same across all solute trajectories.
+  	\item Zero the trajectories. First, zero out the $y$ dimension by rotating each segment of 
+  	the trajectory, as partitioned before clustering, about the $z$ axis, in order to align the 
+  	mean $xy$ vector with the $x$ axis (see Figure~\ref{fig:y_zeroed}). Then, subtract the mean in
+  	$x$ and $z$ (Figure~\ref{fig:xyz_zeroed}.
   	\item Fix clustered state sequence and infer parameters of each state, assuming a mean of zero
-  	for all states (see Figure~\ref{fig:zeroed_hmm}). 
+  	for all states (see Figure~\ref{fig:zeroed_clustered_hmm}). 
   \end{enumerate}
@@
     \centering
-	\begin{subfigure}{0.8\textwidth}
+	\begin{subfigure}{0.6\textwidth}
 	\includegraphics[width=\textwidth]{xyz_hmm.pdf}
@@
 	\end{subfigure}  
-	\begin{subfigure}{0.8\textwidth}
-		\includegraphics[width=\textwidth]{rz_hmm.pdf}
-		\caption{}\label{fig:rz_hmm}
+		\begin{subfigure}{0.6\textwidth}
+		\includegraphics[width=\textwidth]{y_zeroed.pdf}
+		\caption{}\label{fig:y_zeroed}
 	\end{subfigure}  	
-	\begin{subfigure}{0.8\textwidth}
-		\includegraphics[width=\textwidth]{zeroed_hmm.pdf}
-		\caption{}\label{fig:zeroed_hmm}
+	\begin{subfigure}{0.6\textwidth}
+		\includegraphics[width=\textwidth]{xyz_zeroed.pdf}
+		\caption{}\label{fig:xyz_zeroed}
+	\end{subfigure}  		
+	\begin{subfigure}{0.6\textwidth}
+		\includegraphics[width=\textwidth]{zeroed_clustered_hmm.pdf}
+		\caption{}\label{fig:zeroed_clustered_hmm}
 	\end{subfigure}  

### 2020-05-11 Ben_Manuscripts/hdphmm/Draft.tex
comments on draft.

@@
   %link to where she stores the code. Would that be best in the form of a reference?
+  %MRS3: I was thinking of citing YOUR code here.
   Therefore, we looked for convergence of the parameters in Equation~\ref{eqn:var}.
@@
   center-of-mass from the pore center in 2 dimensions, $x$ and $y$. By working in 
-  Cartesian coordinates, we avoid mathematical complexity introduced by cylindrical 
+  Cartesian coordinates, we avoid mathematical complexity introduced by change of coordinates into cylindrical 
   coordinates while estimating the state sequence.
-  %BJC3: maybe could say something about multivariate guassian noise with VAR in cylindrical doesnt work with current code.
+  %BJC3: maybe could say something about multivariate Gaussian noise with VAR in cylindrical doesn't work with current code.
+  %MRS3: tweaked above, probably OK.
 
@@
 
+  %MRS3: I think these belong after clustering.
+
   %BJC3: expanded
@@
   To take advantage of the system's cylindrical symmetry, we converted the parameters that
-  are directly related to solute position into cylindrical coordinates before clustering. We 
-  converted the $x$ and $y$ eigenvalues of $\Sigma$ and $A$ as $\lambda_x$ + $\lambda_y$
-  and $\lambda_x^2$ + $\lambda_y^2$ respectively. %BJC3: possibly could use some justification of these definitions. 
-  We obtained means in $r$, $\mu_r$, using the norm of the $x$ and $y$ means, 
-  $\sqrt{\mu_x^2 + \mu_y^2}$. We squared $\mu_r$ for clustering in order to cast it in the
-  same units as $A$ and $\Sigma$.
+  are directly related to solute position into cylindrical coordinates before clustering. 
+  %MRS3: tweaked: 
+  %We converted the $x$ and $y$ eigenvalues of $\Sigma$ and $A$ as $\lambda_x$ + $\lambda_y$
+  We replaced the $x$ and $y$ eigenvalues of $\Sigma$ and $A$ with
+  $\lambda_x$ + $\lambda_y$ and $\lambda_x^2$ + $\lambda_y^2$
+  respectively, which are invariant with rotation around the $z$ axis,
+  in both cases reducing the dimensionality from 3 to 2.  We clustered
+  on squared means in $r$, $\mu_r^2 = \mu_x^2 + \mu_y^2$, rather than
+  $\mu_x$ and $\mu_y$ individually, with the square $\mu_r$ converting
+  it into the same units as $A$ and $\Sigma$.
 
@@
   %BJC3: modified
-  We remapped and fixed the state sequence based on the cluster assignments and
-  parameterized the clusters using the inference component of the IHMM algorithm. 
-  First, we modified the ($x$, $y$, $z$) solute trajectories so that they had a 
-  mean of zero, leaving only the fluctuations. First, we zeroed the $y$ component
-  of the trajectories by rotating the coordinates about the pore axis such that 
-  the mean vector of each separate segment was aligned with the $x$ axis. Next, 
-  we subtracted the means from each separate segment in the $x$ and $z$ dimensions.
-  We used the IHMM algorithm on this modified trajectory to infer the clustered 
-  state parameters by fixing the clustered state sequence.
+
+  We remapped and fixed the state sequence based on
+  the cluster assignments and parameterized the clusters using the
+  inference component of the IHMM algorithm.  First, we modified the
+  ($x$, $y$, $z$) solute trajectories so that they had a mean of zero,
+  leaving only the fluctuations. Next, we took advantage of the
+  rotational invariance of the system by rotating the
+  coordinates about the pore axis such that the mean vector of each
+  separate segment was aligned with the $x$ axis. Next, we subtracted
+  the means from each separate segment in the $x$ and $z$ dimensions,
+  with the mean in $y$ being zeroed by the rotation.  We used the IHMM
+  algorithm on this modified trajectory to infer the clustered state
+  parameters by fixing the clustered state sequence.
 
@@
   each value of the rotated $\mathbf{c}$ vectors assigned to the same cluster. Note
-  that we only care about the $x$ and $y$ component of $\mathbf{c}$ because solute 
+  %MRS: tweaked
+  that we only care about the $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$ because solute 
   trajectories are not bound in the $z$ direction.
@@
   % the same line as where the next paragraph starts?
+  %MRS3: yes, that's what I'm thinking of.
   \subsubsection*{Deviations of the IHMM from Molecular Motion}
@@
   % some discussion of this to previous section.
-  %MRS: methanol yellow is hard to see in (b). Maybe add outlines to histogram?  I guess they are, increase alpha or something for yello?
+  %MRS: methanol yellow is hard to see in (b). Maybe add outlines to histogram?  I guess they are, increase alpha or something for yellow?
   %MRS: check consistency of capitalization in legend in (c) 
@@
 % LocalWords:  nanostructure carboxylate VMD nonidealities hbonds outlier GAANN
-% LocalWords:  autogregressive PRF ACS XSEDE ACI
+% LocalWords:  autogregressive PRF ACS XSEDE ACI IHMM nanoporous flowback evy
+% LocalWords:  timescale subdiffusive coscia subdiffusion calderon GROMACS der
+% LocalWords:  berendsen gromacs spoel hess emailed plateauing hmm ne gelman AR
+% LocalWords:  walt numpy GCL URE ACH IMMM subsubsection modT convective vmd Na
+% LocalWords:  scannable subsubcaptions errorbars uncharacteristicness facelift
+% LocalWords:  PSC RMACC hdphmm TOC

### 2020-05-13 Ben_Manuscripts/hdphmm/Draft.tex
New explanations

@@
   would be greatly enhanced by easily interpretable methods for connecting microscopic
-  fluctuations with macroscopic observables.
-  \begin{itemize}
-  	\item If one could apply molecular dynamics (MD) simulations to explain important
-  	experimental metrics such as solute flux and selectivity in terms of detailed 
-  	chemically dependent solute motion, then we can more easily bridge the disconnect
-  	between theory and application.
-  	\item In many systems, it's possible to achieve this by calculating diffusion 
-  	constants.%\cite{}
-  	\item Unfortunately, for systems which exhibit complex short timescale 
-  	subdiffusive dynamics, one cannot calculate reliable diffusion 
-  	constants since solute mean square displacements (MSDs) are non-linear 
-    on the timescales accessible to molecular simulation.
-  	\item Therefore, we are in need of a more flexible approach for modeling solute 
-  	dynamics which makes less assumptions about the solute's average behavior.
-  \end{itemize}
+  fluctuations with macroscopic observables. If one could apply molecular dynamics 
+  (MD) simulations to explain important experimental metrics such as solute flux and 
+  selectivity in terms of detailed chemically dependent solute motion, then we can more
+  easily bridge the disconnect between theory and application. In many systems, it's 
+  possible to achieve this by calculating diffusion constants. Unfortunately, for 
+  systems which exhibit complex short timescale subdiffusive dynamics, one cannot 
+  calculate reliable diffusion constants since solute mean square displacements (MSDs)
+  are non-linear on the timescales accessible to molecular simulation. Therefore, we
+  are in need of a more flexible approach for modeling solute dynamics which makes 
+  less assumptions about the solute's average behavior.
 
@@
     \item The IHMM has not been used much for MD trajectory analysis.
-
   \end{itemize}
@@
   parameters for each state and the overall state transition probability matrix, $T$.
-  We created a Python implementation of this process which we heavily adapted from
+  We created a Python implementation of this process 
+  (\texttt{https://github.com/bencoscia/hdphmm}) which we heavily adapted from
   the MATLAB code of Fox et al.~\cite{fox_bayesian_2010} Parameter estimation is iterative. 
@@
   %MRS3: I was thinking of citing YOUR code here.
+  %BJC4: Ah, OK. I plan to fork it into the shirtgroup repo after we submit. Can change link after reviews.
+  %BJC4: Okay to put link? Or should I cite it as a reference?
   Therefore, we looked for convergence of the parameters in Equation~\ref{eqn:var}.
@@
 
-  % BJC3: Cut this paragraph
-%  We carefully applied the IHMM algorithm in a way which takes advantage of the
-%  system's cylindrical symmetry. While there are a number of viable ways in which
-%  one could choose to analyze these time series, we chose to use a multi-step 
-%  procedure that we believe adequately distinguishes the diversity of dynamical 
-%  behavior exhibited by the solutes. The final parameterization of the model is 
-%  in cylindrical coordinates since each pore is a cylinder where we expect 
-%  solutes to exhibit radially symmetric dynamics. We present a step-by-step 
-%  demonstration of the procedure that follows in 
-%  Section~\ref{S-section:ihmm_procedure} of the Supporting Information.
-
   We start by applying the IHMM algorithm to the 3D solute center-of-mass coordinate 
@@
   center-of-mass from the pore center in 2 dimensions, $x$ and $y$. By working in 
-  Cartesian coordinates, we avoid mathematical complexity introduced by change of coordinates into cylindrical 
-  coordinates while estimating the state sequence.
-  %BJC3: maybe could say something about multivariate Gaussian noise with VAR in cylindrical doesn't work with current code.
-  %MRS3: tweaked above, probably OK.
+  Cartesian coordinates, we avoid mathematical complexity introduced by change of 
+  coordinates into cylindrical coordinates while estimating the state sequence.
 
@@
 
-  % BJC3: This paragraph no longer necessary
-%  We reparameterized the time series, preserving the state sequence, in terms
-%  of the radial and axial coordinates ($r$, $z$) due to the system's radial 
-%  symmetry. We converted the $x$ and $y$ center-of-mass coordinates to $r$. 
-%  We fixed the state sequence from the 3D parameterization and applied the 
-%  inference component of the IHMM procedure to the cylindrical trajectories 
-%  in order to estimate the VAR(1) parameters in terms of $r$ and $z$. Since
-%  we fixed the state sequence, and we are using conjugate priors, the VAR 
-%  parameters converge very quickly (see Figure~\ref{S-fig:fixed_state_convergence}).
-%  Therefore, we only ran the inference procedure for 100 iterations. 
-%  % MRS: hmm. Here the new covariance parameters is redone in r - does there need to be any transformation applied? 
-%  % MRS: though might be OK, since x^2 + y^2 = r^2 so maybe covariance are additive if x and y uncorrelated (which they should be)
-%  % MRS2: As I mentioned before, the issue is if the likelihood for the covariance matrix is properly defined for radial diffusion.
-We can check over the equations.
-It likely wouldn't change the qualitative results much, but should ne checked.
-Would not affect the clustering.
-%  We defined the final parameters of each state as the mean of the parameters 
-%  from each iteration recorded after the equilibration time point. We found the 
-%  equilibration time point of each component of the $\mathbf{c}$ vector as well as 
-%  $A$ and $\Sigma$ matrices, and then used the longest equilibration time of all 
-%  dimensions as the equilibration time point.
-
-  \subsubsection*{Predicting Mean Squared Displacement}\label{method:realizations}
-
-  %MRS3: I think these belong after clustering.
-
-  %BJC3: expanded
-  \textit{Generating Stochastic IHMM Trajectory Realizations}: For each independent 
-  MD trajectory, we generated stochastic trajectory realizations using the finalized 
-  parameters of the associated IHMM. We drew state sequences with transition probabilities
-  given by $T$. While in a given state, we simulated motion according to the VAR(1) 
-  parameterization of that state. After each state transition, we set the unconditional
-  mean of the new state to the particle's position immediately before the state 
-  transition occurred.
-
-  %BJC3: this is new, not sure of clarity
-  \textit{Calculating MSD}: The MSD reported for each solute measured by our MD 
-  simulations is a distribution created from the 24 independent MSD curves. We predicted 
-  MSDs and their uncertainties with our stochastic models by bootstrapping the 
-  distribution of stochastically generated MSDs. For each bootstrap trial, we generated
-  24 independent trajectories using the 24 sets of IHMM parameters. We report the mean
-  and standard error of the bootstrapped MSD distributions.
+%  It is important not to view the IHMM as a black box. One should verify that the
+%  model produces qualitative and quantitative results that are accurate on a
+%  trajectory-by-trajectory basis.
+%  \begin{itemize}
+%    \item If the state sequence is not properly partitioned it can lead to 
+%    poor estimates of the transition matrix.
+%    \item In the supporting information, we demonstrate this and provide techniques
+%    for ensuring good state partitioning.
+%  \end{itemize}
 
@@
   of the Supporting Information), which could cause the clustered model to combine 
-  distinct behavior into a non-existent hybrid state.
-  %MRS: not clear what the consequence of the above is?
-  %BJC3: added a little to the end
-
-  %BJC3: reworked the following and split into paragraphs
+  distinct behavior into a non-physical hybrid state.
+
   We clustered based on the eigenvalues of $A$ and $\Sigma$, the distance from the 
@@
   are directly related to solute position into cylindrical coordinates before clustering. 
-  %MRS3: tweaked: 
-  %We converted the $x$ and $y$ eigenvalues of $\Sigma$ and $A$ as $\lambda_x$ + $\lambda_y$
-  We replaced the $x$ and $y$ eigenvalues of $\Sigma$ and $A$ with
-  $\lambda_x$ + $\lambda_y$ and $\lambda_x^2$ + $\lambda_y^2$
-  respectively, which are invariant with rotation around the $z$ axis,
-  in both cases reducing the dimensionality from 3 to 2.  We clustered
-  on squared means in $r$, $\mu_r^2 = \mu_x^2 + \mu_y^2$, rather than
-  $\mu_x$ and $\mu_y$ individually, with the square $\mu_r$ converting
-  it into the same units as $A$ and $\Sigma$.
+  We replaced the $x$ and $y$ eigenvalues of $\Sigma$ and $A$ with $\lambda_x$ + 
+  $\lambda_y$ and $\lambda_x^2$ + $\lambda_y^2$ respectively, which are invariant with 
+  rotation around the $z$ axis, in both cases reducing the dimensionality from 3 to 2.  
+  We clustered on squared means in $r$, $\mu_r^2 = \mu_x^2 + \mu_y^2$, rather than
+  $\mu_x$ and $\mu_y$ individually, with the square $\mu_r$ converting it into the 
+  same units as $A$ and $\Sigma$.
 
@@
   1. Therefore we found the most success with agglomerative clustering by linearizing this
-  relationship and clustering on $-\log(1 - T_{ii})$ (see Section~\ref{S-section:selfT_cluster}
-  of the Supporting Information for a graphical illustration).
-
-%  One can choose alternative clustering
-%  features, such as the eigenvalues of the $A$ and $\Sigma$ matrices, but we chose their 
-%  diagonals because they can be easily translated to solute behavior. The diagonals of $A$
-%  describe the correlation between sequential hops while the diagonals of $\Sigma$ describe
-%  the size of the hops in each dimension. We assume that cross correlations in the parameters
-%  are negligible for clustering.
-%   
-%  We also chose to cluster the diagonals of each matrix and the radial means
-%  independently before combining the clusters to assign final state labels. If we divide
-%  the total states into $m$ clusters based on the diagonal entries of $A$, $n$ more clusters 
-%  based on the diagonal entries of $\Sigma$, and $k$ clusters based on $\mu_r$, then there
-%  are a total of $mnk$ possible cluster combinations. This allows slightly more flexibility
-%  in the total number of states compared to clustering on all five features at once, since 
-%  there can be up to, but not necessarily exactly, $mnk$ states.
+  relationship and clustering on $-\log(1 - T_{ii})$.
+  % (see Section~\ref{S-section:selfT_cluster} of the Supporting Information for a graphical illustration).
+
+  %BJC4: Added
+  There are alternative ways to cluster the data dependent on one's goals. Our goal is
+  to derive the simplest set of parameter which adequately describe solute motion. 
+  However, one may want a more detailed understand of specific dimensions of the 
+  clustering dataset. In this case one can cluster on one or more dimensions independently
+  and then enumerate the possible clusters. This would ensure very little overlap of
+  clusters but may result in a large number of them. Once one has achieved a better 
+  understanding of solute-membrane interactions, perhaps by using the iHMM, it may be
+  beneficial to incorporate other physically motivated variables into the clustering
+  procedure. For example, one can gain a thorough understanding of the dynamics of
+  different kinds of trapping behavior related to hydrogen bonding and sodium ion association.
 
@@
 
-  Choosing the number of clusters can be somewhat subjective so
-  we attempted to add some structure to the selection process by following
-  a set of qualitative and quantitative guidelines. We used the silhouette 
-  test in order to score the quality of clustering as a function of the number 
-  of clusters chosen.~\cite{kaufman_finding_2009} For our data, the silhouette 
-  test generally favors the lowest number of clusters possible (see 
-  Section~\ref{S-section:nclusters} of the Supporting Information). However, 
-  choosing too few clusters tends to not distinguish between visually obvious 
-  differences in dynamic behavior. This results in finalized parameter sets 
-  that are averages of distinct behavior which presents further problems with 
-  the predictive modeling that we discuss later on. We aimed to maintain the 
-  highest silhouette score, and thus lowest number of clusters, possible while
-  verifying that visually distinct states stayed separated.
+  Choosing the number of clusters can be somewhat subjective so we attempted to add some
+  structure to the selection process by following a set of qualitative and quantitative 
+  guidelines. We give an in depth justification of our clustering choices in 
+  Section~\ref{S-section:nclusters} of the Supporting Information. We used the silhouette
+  test in order to score the quality of clustering as a function of the number of clusters
+  chosen.~\cite{kaufman_finding_2009} For our data, the silhouette test generally favors 
+  the lowest number of clusters possible. However, choosing too few clusters tends to not
+  distinguish between visually obvious differences in dynamic behavior. This can result 
+  in finalized parameter sets that are averages of distinct behavior which presents 
+  further problems with the predictive modeling that we discuss later on.
+
+  %BJC4: added
+  We aimed to maintain the highest silhouette score, and thus lowest number of clusters,
+  possible while preserving the dynamics of each trajectory.
+  %verifying that visually distinct states stayed separated. 
+  We verified preservation of the dynamics by comparing the MSDs of stochastic trajectory
+  realizations based on clustered IHMM parameter sets to the pooled MSDs of stochastic 
+  realizations of IHMMs fit to individual trajectories (see Section~\ref{method:realizations}).
+  We chose the lowest number of clusters that reasonably reproduced the pooled MSDs at 
+  short and long time lags (See Figure~\ref{S-fig:MET_nclusters} of the Supporting 
+  Information).
 
@@
 
-  We remapped and fixed the state sequence based on
-  the cluster assignments and parameterized the clusters using the
-  inference component of the IHMM algorithm.  First, we modified the
-  ($x$, $y$, $z$) solute trajectories so that they had a mean of zero,
-  leaving only the fluctuations. Next, we took advantage of the
-  rotational invariance of the system by rotating the
-  coordinates about the pore axis such that the mean vector of each
-  separate segment was aligned with the $x$ axis. Next, we subtracted
-  the means from each separate segment in the $x$ and $z$ dimensions,
-  with the mean in $y$ being zeroed by the rotation.  We used the IHMM
-  algorithm on this modified trajectory to infer the clustered state
-  parameters by fixing the clustered state sequence.
-
-  We obtained $\mathbf{c}$ vectors of the clustered states by averaging 
-  each value of the rotated $\mathbf{c}$ vectors assigned to the same cluster. Note
-  %MRS: tweaked
-  that we only care about the $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$ because solute 
-  trajectories are not bound in the $z$ direction.
-
-  \subsection{Tools for using the Parameterized Model to Explore Mechanisms}\label{method:interactions}
-
-  We determined the number of hydrogen bonds between each solute and the membrane
-  as a function of time. Based on the geometric criteria of Luzar and Chandler, we 
-  define a hydrogen bond to exist if the distance between donor, D, and acceptor, 
-  A, atoms is less than 3.5\AA~and the angle formed by $D-H \cdots A$ is less than 
-  $30\degree$.~\cite{luzar_effect_1996}
-
-  We estimated the lifetime of hydrogen bonds by recording the length of 
-  sequential frames where solutes remained hydrogen bonded. We still counted sequences
-  where hydrogen bonds were broken for a single frame before reforming. Consistent
-  with our previous work, we reported the 95th percentile of hydrogen bond lifetimes
-  since their distribution is not Gaussian and to emphasize longer trapping periods.~\cite{coscia_chemically_2019}
-
-  We also measured the degree of association between solutes and sodium ions on a
-  frame-by-frame basis. We define a sodium ion to be associated with an atom if they
-  are within 2.5 \AA~of each other, as determined in our previous work.~\cite{coscia_chemically_2019}
-
-  %We developed a way to 
-  We measure the local density of the membrane at arbitrary
-  points in the unit cell as follows. We histogrammed the positions in three dimensions
-  Since our system is in a monoclinic unit cell, we periodically replicated
-  the system in the $\pm x$, $y$ and $z$ directions and then chose the bounds on the
-  histogram in order to create a rectangular box encompassing the unit cell with
-  a 1 nm buffer between the histogram and unit cell boundaries.~\cite{van_der_walt_numpy_2011} We then used a regular
-  grid interpolator in order to allow interpolation at arbitrary points within the grid.~\cite{virtanen_scipy_2020}
-
-  We quantified solute motion using the time averaged mean squared displacement (MSD)
+  We remapped and fixed the state sequence based on the cluster assignments and 
+  parameterized the clusters using the inference component of the IHMM algorithm.
+  First, we modified the ($x$, $y$, $z$) solute trajectories so that they had a 
+  mean of zero, leaving only the fluctuations. Next, we took advantage of the
+  rotational invariance of the system by rotating the coordinates about the pore 
+  axis such that the mean vector of each separate segment was aligned with the 
+  $x$ axis. Next, we subtracted the means from each separate segment in the $x$ 
+  and $z$ dimensions, with the mean in $y$ being zeroed by the rotation. We used
+  the inference component of the IHMM algorithm on this modified trajectory to 
+  infer the clustered state parameters by fixing the clustered state sequence.
+
+  We obtained $\mathbf{c}$ vectors of the clustered states by averaging each 
+  value of the rotated $\mathbf{c}$ vectors assigned to the same cluster. Note
+  that we only care about the $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$ because
+  solute trajectories are not bound in the $z$ direction.
+
+  \subsection{Predicting Mean Squared Displacement}\label{method:realizations}
+
+  \textit{Generating Stochastic IHMM Trajectory Realizations}: For each independent 
+  MD trajectory, we generated stochastic trajectory realizations using the finalized 
+  parameters of the associated IHMM. We drew state sequences with transition probabilities
+  given by $T$. While in a given state, we simulated motion according to the VAR(1) 
+  parameterization of that state. After each state transition, we set the unconditional
+  mean of the new state to the particle's position immediately before the state 
+  transition occurred.
+
+  \textit{Calculating MSD}: We quantified solute motion using the time averaged mean squared displacement (MSD)
   of the solute center of mass trajectories.~\cite{meroz_toolbox_2015} The time-averaged MSD measures all observed
@@
 
+  The MSD reported for each solute measured by our MD 
+  simulations is a distribution created from the 24 independent MSD curves. We predicted 
+  MSDs and their uncertainties with our stochastic models by bootstrapping the 
+  distribution of stochastically generated MSDs. For each bootstrap trial, we generated
+  24 independent trajectories using the 24 sets of IHMM parameters. We report the mean
+  and standard error of the bootstrapped MSD distributions.
+
+  \subsection{Tools for using the Parameterized Model to Explore Mechanisms}\label{method:interactions}
+
+  We determined the number of hydrogen bonds between each solute and the membrane
+  as a function of time. Based on the geometric criteria of Luzar and Chandler, we 
+  define a hydrogen bond to exist if the distance between donor, D, and acceptor, 
+  A, atoms is less than 3.5\AA~and the angle formed by $D-H \cdots A$ is less than 
+  $30\degree$.~\cite{luzar_effect_1996}
+
+  We estimated the lifetime of hydrogen bonds by recording the length of 
+  sequential frames where solutes remained hydrogen bonded. We still counted sequences
+  where hydrogen bonds were broken for a single frame before reforming. Consistent
+  with our previous work, we reported the 95th percentile of hydrogen bond lifetimes
+  since their distribution is not Gaussian and to emphasize longer trapping periods.~\cite{coscia_chemically_2019}
+
+  We also measured the degree of association between solutes and sodium ions on a
+  frame-by-frame basis. We define a sodium ion to be associated with an atom if they
+  are within 2.5 \AA~of each other, as determined in our previous work.~\cite{coscia_chemically_2019}
+
+  %We developed a way to 
+  We measure the local density of the membrane at arbitrary
+  points in the unit cell as follows. We histogrammed the positions in three dimensions
+  Since our system is in a monoclinic unit cell, we periodically replicated
+  the system in the $\pm x$, $y$ and $z$ directions and then chose the bounds on the
+  histogram in order to create a rectangular box encompassing the unit cell with
+  a 1 nm buffer between the histogram and unit cell boundaries.~\cite{van_der_walt_numpy_2011} We then used a regular
+  grid interpolator in order to allow interpolation at arbitrary points within the grid.~\cite{virtanen_scipy_2020}
+
   \section{Results and Discussion}
@@
   We applied the IHMM independently to all 24 trajectories of each of the four solutes studied.
-  \begin{itemize}
-    \item The number of states found for each trajectory varied between 5 and 30  %BJC2: need to see what these numbers actually are.
-    \item In Figure~\ref{fig:rz_unclustered}, we show the state sequence determined by the
-    IHMM for an example methanol trajectory.
-    \item The model distinguished many of the states due to differences in their mean levels 
-    while their fluctuations about those means are often similar. 
-    \item In Section~\ref{section:mechanisms}, we use clustering to reduce the total state
-    space for each solute.    
-  \end{itemize}
-
+  The number of states found for each trajectory varied between 5 and 30.  %BJC2: MET: (5, 28)
+  In Figure~\ref{fig:rz_unclustered}, we show the state sequence determined by the IHMM for
+  an example methanol trajectory. The model distinguishes many of the states due to 
+  differences in their mean levels while their fluctuations about those means are often 
+  similar. In Section~\ref{section:mechanisms}, we use clustering to reduce the total state
+  space for each solute in order to more easily interpret the state parameters.
+
+  %BJC4: It might be good to add a panel to this figure which gives a radial view of the pore
   \begin{figure}
@@
   \includegraphics[width=\textwidth]{rz_unclustered_MET.pdf}
-  \caption{The IHMM found 24 distinct VAR(1) states in this representative methanol trajectory.}\label{fig:rz_unclustered}
+  \caption{The IHMM found 24 distinct VAR(1) states in this representative methanol trajectory.
+  We performed the parameterization in 3D cartesian coordinates, but for this figure, we 
+  converted to cylindrical coordinates, with $r$ the distance from the pore center, to 
+  provide a clearer picture of solute motion.}\label{fig:rz_unclustered}
   \end{figure}
 
-  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}
-
-  % MRS: maybe makes sense to talk a little about what features/parameters of the 
-  % models the MSD is sensitive to?
+  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}\label{section:unclustered_MSD_prediction}
 
@@
   IHMM, it is important to verify whether the state dynamics are consistent with MD
-  both qualitatively and quantitatively.
-  \begin{itemize}
-    \item Therefore, we generated stochastic realizations based on the parameters 
-    of each trajectory as described in Section~\ref{method:realizations}.
-  \end{itemize}
+  both qualitatively and quantitatively. Therefore, we generated stochastic 
+  realizations based on the parameters of each trajectory as described in 
+  Section~\ref{method:realizations}.
 
@@
   can produce trajectories that show qualitatively similar hopping and trapping 
-  behavior to the MD trajectories.
-  \begin{itemize}
-    \item It is important that our model reproduces this behavior so that we can
-    have confidence in its usefulness for quantitative predictions.
-  \end{itemize}
-
+  behavior to the MD trajectories. It is important that our model reproduces this 
+  behavior so that we can have confidence in its usefulness for quantitative 
+  predictions.
+
+  % BJC4: This figure needs to be redone with new trajectory generation procedure
   \begin{figure}
@@
 
-  \noindent From a quantitative standpoint, the model has two shortcomings.
-  \begin{itemize}
-  	\item First, in many cases, the MSD predicted by realizations of the IHMM 
-  	under-predicts that of MD (see Figure~\ref{fig:unclustered_msds}).
-  	\item Second, the shapes of the MSD curves at short time lags are very different.
-  \end{itemize}
+  \textit{Deviations of the IHMM from Molecular Motion}: From a quantitative
+  standpoint, using the IHMM as a predictive tool has two 
+  shortcomings. First, in many cases, the MSD predicted by realizations of the 
+  IHMM under-predicts that of MD (see Figure~\ref{fig:unclustered_msds}).
+  Second, the shapes of the MSD curves at short time lags are very different.
 
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.24\textwidth}
   \includegraphics[width=\textwidth]{unclustered_msd_MET.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.24\textwidth}
   \includegraphics[width=\textwidth]{unclustered_msd_GCL.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.24\textwidth}
   \includegraphics[width=\textwidth]{unclustered_msd_URE.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.24\textwidth}
   \includegraphics[width=\textwidth]{unclustered_msd_ACH.pdf}
@@
   the IHMM (orange), while the predictions match within uncertainty for ethylene
-  glycol and urea.}\label{fig:unclustered_msds}
-  %MRS2: to save space, could consider the graphs in 1x4 across the top, with a single legend (since all have the same), and slightly thicker lines  %There are only 2 lines per plot, so it's not too noisy to be that size
-  %BJC3: good point
+  glycol and acetic acid}\label{fig:unclustered_msds}
   \end{figure}
 
-  %MRS2: I'd make this a separate subsection ``Deviations of the IMMM from molecular motion'' or something like that.
-  % BJC3: would these subsubsection headers look better as just italicized and on 
-  % the same line as where the next paragraph starts?
-  %MRS3: yes, that's what I'm thinking of.
-  \subsubsection*{Deviations of the IHMM from Molecular Motion}
-
-  \noindent The IHMM under-predicts MD MSD due to its tendency to favor fewer states.%\cite{}
-  \begin{itemize}
-    \item Disjoint segments with similar VAR parameters, but different lengths of 
-    entrapment can be parameterized as the same state.
-    \item In Figure~\ref{fig:dwell_distributions}, we compare the overall dwell 
-    time distributions generated directly from MD simulations to that generated from 
-    realizations of the IHMM. 
-    \item Some of the probability density of short trapping times in the MD simulations
-    gets shifted to medium length trapping times in realizations of the IHMM.
-    \item In Figure~\ref{fig:dwell_distributions_modT} and~\ref{fig:msd_modT}, we show 
-    that by modifying the transition matrix to encourage transitions towards states with
-    shorter dwell times, we can more closely reproduce the dwell time distribution and 
-    MSD of MD.
-    \item This is because most solute motion is a consequence of transitions between 
-    trapped states.
-  \end{itemize}
+  The IHMM under-predicts the MD MSD due to its tendency to favor fewer states. 
+  Disjoint segments with similar VAR parameters, but different lengths of entrapment
+  can be parameterized as the same state. In Figure~\ref{fig:dwell_distributions}, 
+  we compare the overall dwell time distributions generated directly from MD simulations to that 
+  generated from realizations of the IHMM. We do this by measuring the time spent in 
+  each independent same-state segment. Some of the probability density of short 
+  trapping times in the MD simulations gets shifted to medium length trapping times
+  in realizations of the IHMM. In Figure~\ref{fig:dwell_distributions_modT} 
+  and~\ref{fig:msd_modT}, we show that by modifying the transition matrix to 
+  encourage transitions towards states with shorter dwell times, we can more closely
+  reproduce the dwell time distribution and MSD of MD. This is because most solute
+  motion is a consequence of transitions between trapped states.
+
+  % BJC4: A lower priority supporting information section I've had in mind is one
+  % with tips for fitting and validating the IHMM on individual trajectories.  
+%  In many cases, especially evident where MSD predictions over-estimate MD, there
+%  is some error in the state sequence segmentation. In Section~\ref{S-section:fitting_tips}
+%  of the Supporting Information, we give some tips based on our experience of how to 
+%  initialize IHMM fits in order to reduce error.
 
@@
   \caption{(a) The density of short dwell times compiled from realizations of
-  the IHMM is below that measured directly from the MD trajectories. If we
-  modify the transition matrix in order to favor transitions towards states with
-  short dwell times, we can more closely match the (b) dwell time distributions
-  and (c) MSDs.}\label{fig:slow_T}
+  the IHMM fit to methanol trajectories is below that measured directly from 
+  the MD trajectories. If we modify the transition matrix in order to favor 
+  transitions towards states with short dwell times, we can more closely match
+  the (b) dwell time distributions and (c) MSDs.}\label{fig:slow_T}
   \end{figure}
 
-  At extremely short time lags, the MSD is generally over-predicted by the IHMM,
-  see Figure~\ref{fig:unclustered_msd_shortlag}, because the VAR(1) model assumes
+  At extremely short time lags, the MSD is generally over-predicted by the IHMM
+  (see Figure~\ref{fig:unclustered_msd_shortlag}) because the VAR(1) model assumes
   multivariate Gaussian noise while the MD data suggests the noise is better 
-  modeled by more general L\'evy stable noise.
-  \begin{itemize}
-    \item The first time lag of the MSD is effectively the variance of all 
-    observed fluctuations. 
-    \item The IHMM simulation appears to over-estimate the variance because the 
-    actual distribution of hops has heavy tails with a smaller variance. (Figure~\ref{fig:emission_widths}).
-    \item The total distribution of hops is expected to be heavy tailed because
-    it is a combination of hop distributions from many state with different variances. 
-    \item More interestingly, in Figure ~\ref{fig:state_emission_widths}, we show that
-    the emission distribution of a single state picked out by the IHMM is fit better by
+  modeled by more general L\'evy stable noise. The first time lag of the MSD is
+  equivalent to the variance of all observed fluctuations (first-order difference). 
+  The IHMM simulation appears to over-estimate the variance because the actual 
+  distribution of solute fluctuations has heavy tails with a smaller variance. (Figure~\ref{fig:emission_widths}).
+  The total distribution of hops is expected to be heavy tailed because it is a
+  combination of hop distributions from many states with different variances. More
+  interestingly, in Figure ~\ref{fig:state_emission_widths}, we show that the 
+  emission distribution of a single state picked out by the IHMM is fit better by
   a more general L\'evy distribution while the emissions from IHMM realizations are
-    Gaussian, as expected.
-    \item An improvement to the IHMM that may allow dynamics more faithful to MD would
-    using an autoregressive model with L\'evy stable noise. However this would be 
-    less computationally efficient to lack of conjugate priors.
-  \end{itemize}
+  Gaussian, as expected. An improvement to the IHMM that may allow dynamics more 
+  faithful to MD would use an autoregressive model with L\'evy stable noise. However,
+  this would be less computationally efficient due to lack of conjugate priors.
 
@@
   differ significantly in their shape and curvature. (b) While the 
-  fluctuations in $z$ of both distributions are heavy-tailed, fitting well to L\'evy
-  stable distributions, the IHMM has a wider variance. (c) The distribution of 
-  fluctuations in a state frequently visited by methanol is heavy tailed, but the 
-  IHMM is constrained to producing fluctuations from a Gaussian distribution ($\alpha$=2).
+  fluctuations in $z$ of both distributions are heavy-tailed, fitting well to zero-centered
+  symmetric L\'evy stable distributions with stability parameters, $\alpha$, the IHMM has
+  a wider variance. (c) The distribution of fluctuations in a chosen state frequently
+  visited by methanol is heavy tailed, but the IHMM is constrained to produce fluctuations
+  from a multivariate normal distribution ($\alpha$=2 in each dimension).
   }\label{fig:short_timelags}
@@
   curvature of the MD MSD is far more gradual than that generated by the IHMM.
-  \begin{itemize}
-    \item This is because the VAR(1) model is only correlated to its previous
-    fluctuation while the MD simulations suggest that correlation persists for
-    at least tens of nanoseconds.
+  This is because the VAR(1) model is only correlated to its previous fluctuation
+  while the MD simulations suggest that correlation persists for at least tens
+  of nanoseconds.
     % BJC2: could probably use a correlation function to suggest the AR order and stick the plot in SI
-    \item One may be able to reproduce the curvature at short time lags with
-    higher order VAR models, but it becomes a much more difficult parameterization
-    that would require significantly more data.
-    \item Since we are interested in longer time scale behavior, it is not an 
-    issue of great concern.
-  \end{itemize}
+  One may be able to reproduce the curvature at short time lags with higher order
+  VAR models, but it becomes a much higher dimensional parameterization that would
+  require significantly more data in order to produce stable results. Since we 
+  are interested in reproducing longer time scale behavior, it is not an issue of
+  great concern.
 
@@
 
-  The ratio of solute fluxes are sufficient to justify
+  We can use the ratio of solute fluxes predicted by realizations of our models in order to 
+  estimate selectivity.
+  \begin{itemize}
+    \item Exact methodology under development
+    \item Will probably just take advantage of long timescale MSD linearity in order to get
+    flux, rather than mean first passage time approach.
+    \item Need to figure out how to deal with differences in MSD under-estimates
+  \end{itemize}
 
@@
   states identified by the IHMM for each solute as described in 
-  Section~\ref{method:clustering}.
-  \begin{itemize}
-    \item In Figure~\ref{fig:mechanism_map}, we show the results of clustering on the same trajectory
-    from Figure~\ref{fig:rz_unclustered}.
-    \item We chose to use X clusters based on the criteria described in 
-    Section~\ref{method:clustering}.  %BJC2: might be some variation between solutes.
-    % BJC2: There will be figures in supporting to help justify number of clusters, but I don't want
-    % to dwell on it at all in the main text.
-    \item Therefore, we reduced the total state space from 300 to X.  %BJC: obviously these numbers will be updated
-    \item By working to understand the parameters of each cluster, we can 
-    gain an understanding of associated solute transport mechanisms responsible for 
-    those parameters.
-  \end{itemize}
-
-%  Using the parameters of the clustered states to generate stochastic realizations
-%  allows us to create representative trajectories which incorporate dynamics of
-%  all 24 solute trajectories.
-%  \begin{itemize}
-%    \item MSD under-predicted compared to unclustered states
-%  \end{itemize}
+  Section~\ref{method:clustering}. In Figure~\ref{fig:mechanism_map}, we show
+  the results of clustering on the same trajectory from 
+  Figure~\ref{fig:rz_unclustered}. We chose to use X clusters based on the
+  criteria described in Section~\ref{method:clustering}. Therefore, we reduced 
+  the total state space from 300 to X. By working to understand the parameters
+  of each cluster, we can gain an understanding of associated solute transport
+  mechanisms responsible for those parameters.
 
   \subsubsection*{Relating Clusters to Mechanisms}
-  %The Dynamics of Methanol}
 

### 2020-05-13 Ben_Manuscripts/hdphmm/Supporting_Information.tex
New explanations

@@
 
-  \subsection{Clustering on the self-transition probabilities}\label{section:selfT_cluster}
+%  \subsection{Clustering on the self-transition probabilities}\label{section:selfT_cluster}
+%  
+%  To cluster on $T_{ii}$, we first cast it in terms of the expected dwell times. The expected 
+%  value of the number of sequential self-transitions is simply $\frac{1}{1 - T_{ii}}$. This 
+%  relationship correctly implies that dwell times approach infinity as $T_{ii}$ approaches 1. 
+%  There we found the most success with agglomerative clustering by linearizing this 
+%  relationship and clustering on $-log(1 - T_{ii})$.
 
-  To cluster on $T_{ii}$, we first
-  cast it in terms of the expected dwell times. The expected value of the number of sequential
-  self-transitions is simply $\frac{1}{1 - T_{ii}}$. This relationship correctly implies that 
-  dwell times approach infinity as $T_{ii}$ approaches 1. There we found the most success with
-  agglomerative clustering by linearizing this relationship and clustering on $-log(1 - T_{ii})$.
+  \subsection{Choosing Linkage Criteria and the Number of Clusters}\label{section:nclusters}
 
-  \subsection{Choosing the Number of Clusters}\label{section:nclusters}
+  In this section, we determine the optimal linkage criteria and number of clusters
+  for studying methanol's parameters. We applied the same workflow to make analogous
+  decisions for ethylene glycol, urea and acetic acid. In all cases, we found that
+  the `ward' linkage criteria resulted in the most useful clustering. We chose to 
+  use x number of clusters for each solute, the minimum number of clusters, by our
+  analysis, needed to adequately distinguish state dynamics.
 
-  \begin{figure}[h]
+  In order to cluster the parameter sets, we need to determine the linkage criteria 
+  that will be used to measure the distance between clusters as well as an appropriate
+  total number of clusters. In Figure~\ref{fig:linkages}, we show the result of clustering
+  with each type of linkage criteria available with the 
+  \texttt{sklearn.cluster.AgglomerativeClustering} class of the \texttt{scikit-learn} 
+  python package. It is clear that both the `average' and `single' linkage criteria 
+  do not sufficiently cluster the data. The `ward' criteria appears to result in the 
+  highest number of large population clusters.
+
+  \begin{figure}
   \centering
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{nclusters_ward.pdf}
+  \caption{`ward'}\label{fig:nclusters_ward}
+  \end{subfigure}
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{nclusters_complete.pdf}
+  \caption{`complete'}\label{fig:silhouette_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{nclusters_average.pdf}
+  \caption{`average'}\label{fig:nclusters_average}
+  \end{subfigure}
+  \begin{subfigure}{0.24\textwidth}
+  \includegraphics[width=\textwidth]{nclusters_single.pdf}
+  \caption{`single'}\label{fig:nclusters_single}
+  \end{subfigure}
+  \caption{In each column we tested a different linkage criteria for clustering
+  of the methanol parameters. In each row, we varied the number of total clusters. 
+  Both `ward' and `complete' linkage appear to induce clustering
+  while the `average' and `single' criteria tend to concentrate parameters in
+  only a fraction of the available clusters.}\label{fig:linkages}
+  \end{figure}
+
+  We can help to further narrow our decision of linkage criteria by analyzing 
+  the parameters of the clusters which it produces. In particular, we should 
+  look for well-distinguished clusters on the radial means so that it will be
+  easier to connect solute behavior to the membrane pore structure. One way to
+  concisely visualize the radial clusters is by their spread. An optimal number
+  of clusters should have the same spread in radial means as the unclustered
+  data. In Figure~\ref{fig:rspread}, we show that `ward' linkage results in 
+  the highest spread in the radials means of the clusters across a range of
+  4--30 total clusters. For a low to intermediate number of clusters, the 
+  spread of `ward' clusters is significantly larger than of the other linkage
+  methods. Therefore, we have chosen to use `ward' clustering.
+
+  We use the Silhouette score in order to aid us in choosing the total number of
+  clusters. In Figure~\ref{fig:silhouette_MET}, we plot the Silhouette score as
+  a function of the total number of clusters using the `ward' linkage criteria. 
+  A Silhouette score of 1 indicates the best clustering possible, values near
+  0 indicate overlapping clusters, and negative values indicate samples belong to
+  the wrong clusters. For the methanol parameters, the Silhouette score drops off
+  quickly with number of clusters before plateauing around 7 total clusters. 
+  However, given the low spread in $\mu_r$, it is not clear that using 7 or less 
+  clusters will give useful clustering results.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.53\textwidth}
+  \includegraphics[width=\textwidth]{rspread_nclusters.pdf}
+  \caption{}\label{fig:rspread}
+  \end{subfigure}
   \begin{subfigure}{0.45\textwidth}
   \includegraphics[width=\textwidth]{silhouette_MET.pdf}
-  \caption{methanol}\label{fig:silhouette_MET}
+  \caption{}\label{fig:silhouette_MET}
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{silhouette_URE.pdf}
-  \caption{urea}\label{fig:silhouette_URE}
+  \caption{(a) The `ward' linkage criteria maintains the highest standard 
+  deviation in radial means, $\mu_r$, of the clusters for a given total 
+  number of clusters as compared to other linkage criteria. (b) The 
+  Silhouette score, used to evaluate the quality of clustering with the 
+  `ward' distance criteria drops precipitously as a function of the chosen
+  total number of clusters before plateauing.}\label{fig:idk}
+  \end{figure}
+
+  We incorporate qualitative feedback into the decision on the number of 
+  clusters. Despite its high Silhouette score, Figure~\ref{fig:4cluster_state_sequence}
+  illustrates that using 4 clusters clearly does not distinguish dynamical 
+  modes. We do not see visually acceptable clustering on the example trajectory
+  until we use at least twenty total clusters (Figure~\ref{fig:20cluster_state_sequence}).
+
+  \begin{figure}
+  \begin{subfigure}{0.9\textwidth}
+  \includegraphics[width=1\textwidth]{clustered_traj_MET_ward_4.pdf}
+  \caption{4 total clusters}\label{fig:4cluster_state_sequence}
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{silhouette_GCL.pdf}
-  \caption{ethylene glycol}\label{fig:silhouette_GCL}
+  \begin{subfigure}{0.9\textwidth}
+  \includegraphics[width=1\textwidth]{clustered_traj_MET_ward_12.pdf}
+  \caption{12 total clusters}\label{fig:12cluster_state_sequence}
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{silhouette_ACH.pdf}
-  \caption{acetic acid}\label{fig:silhouette_ACH}
+  \begin{subfigure}{0.9\textwidth}
+  \includegraphics[width=1\textwidth]{clustered_traj_MET_ward_20.pdf}
+  \caption{20 total clusters}\label{fig:20cluster_state_sequence}
   \end{subfigure}
-  \caption{We used the silhouette score test in order to quantitatively
-  inform our decision on the numbrer of clusters. Silhouette scores 
-  closer to one indicate good clustering. The crosses on the plot indicate
-  our choice in number of clusters after careful consideration of the
-  silhouette scores in conjunction with qualitative examination of the clusters
-  formed by the choice. Although the test often
-  favors fewer states, we elected to use an intermediate number of states in 
-  the cases of $A$ and $\Sigma$ because choosing 2--3 clusters 
-  insufficiently separates the dynamical modes. }\label{fig:silhouette}
+  \caption{Although the Silhouette score for four total clusters is high, we do
+  not see adequate distinction between clusters until we group the parameters
+  from the 24 trajectories into 20 total clusters. When we use 12 total clusters,
+  the distinction appears acceptable except that the segment from ~50--550 ns
+  and from 1200--1500 ns (both colored orange) are clustered together. The radial
+  means of these two segments correspond to two very different morphological
+  regions of the membrane.}\label{fig:clustered_state_sequences}
+  \end{figure}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{nclusters_msd_MET_ward.pdf}
+  \caption{The total MSD predicted by stochastic realizations of the clustered
+  model is relatively insensitive to the total number of clusters. All
+  predictions are less than the predictions of MD and the unclustered trajectories.
+  This behavior is expected due to underestimation of the short dwell time 
+  densities as described in Section~\ref{M-section:unclustered_MSD_prediction}
+  of the main text.}\label{fig:MET_nclusters} 
+  \end{figure}
+
+  This clustering analysis will be finished after some mechanistic studies. It is
+  clear that we will need some understanding of mechanisms in order to 
+  arrive at a cluster recommendation.
+
+%  \begin{figure}[h]
+%  \centering
+%  \begin{subfigure}{0.475\textwidth}
+%  \includegraphics[width=\textwidth]{nclusters_msd_MET_ward.pdf}
+%  \caption{ward}\label{fig:nclusters_msd_MET_ward}
+%  \end{subfigure}
+%  \begin{subfigure}{0.475\textwidth}
+%  \includegraphics[width=\textwidth]{nclusters_msd_MET_complete.pdf}
+%  \caption{complete}\label{fig:nclusters_msd_MET_complete}
+%  \end{subfigure}
+%  \begin{subfigure}{0.475\textwidth}
+%  \includegraphics[width=\textwidth]{nclusters_msd_MET_average.pdf}
+%  \caption{average}\label{fig:nclusters_msd_MET_average}
+%  \end{subfigure}
+%  \begin{subfigure}{0.475\textwidth}
+%  \includegraphics[width=\textwidth]{nclusters_msd_MET_single.pdf}
+%  \caption{single}\label{fig:nclusters_msd_MET_single}
+%  \end{subfigure} 
+%  \caption{}\label{fig:MET_nclusters} 
+%  \end{figure}
+
+  \subsection{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
+
+  The IHMM is quite powerful on its own, but requires some critical thinking by
+  the user in order to ensure maximum effectiveness. One can obtain 
+  the best results with some simple checks and, where necessary, improved 
+  state sequence initialization.
+
+  The best way to ensure reliable MSD predictions is to ensure proper reproduction
+  of the individual MD MSDs by realizations of the IHMM. Over-predictions and 
+  under-predictions are usually the result of a poorly identified state sequence. (see
+  Figure TBD for example)
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.35\textwidth}
+  \includegraphics[width=\textwidth]{overestimate_ACH_21.pdf}
+  \caption{}\label{fig:msd_overestimate}
+  \end{subfigure}
+  \begin{subfigure}{0.63\textwidth}
+  \includegraphics[width=\textwidth]{state_sequence_before_ACH_21.pdf}
+  \caption{}\label{fig:state_sequence_before}
+  \end{subfigure}
+  \begin{subfigure}{0.35\textwidth}
+  \includegraphics[width=\textwidth]{msd_improvement_ACH_21.pdf}
+  \caption{}\label{fig:msd_improvement}
+  \end{subfigure}
+  \begin{subfigure}{0.63\textwidth}
+  \includegraphics[width=\textwidth]{state_sequence_after_ACH_21.pdf}
+  \caption{}\label{fig:state_sequence_after}
+  \end{subfigure}
+  \caption{(a, b) In some cases, the state segmentation leads to over- or 
+  under-prediction of the MSD, usually due to poor initialization of the state
+  sequence. In (b), state transitions are too frequent and lead to an
+  overprediction of the MD MSD. (c) We can greatly improve MSD predictions by
+  giving the IHMM a good guess at the initial state sequence. (d) A better
+  initial state segmentation via seeding, gives more reasonable estimates
+  of the final state sequence.}\label{fig:improvement_state_sequence}
+  \end{figure}
+
+  There are two primary approaches we have implemented in order to improve the final 
+  state sequence predictions. Both attempt to aid the initial state assignments 
+  algorithmically. First, we always initialize the prior on $\mathbf{c}$ in 
+  Equation~\ref{M-eqn:var} of the main text as described in 
+  Section~\ref{section:prior_guesses}. In particularly tricky cases, the initial
+  state sequence estimate is so poor that qualitative trajectory realizations
+  and MSD predictions are irreconcilable with MD. In our second approach, we can
+  seed the initial state sequence with a guess made by applying the IHMM to 
+  smaller segments of the trajectory.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_segment0.pdf}
+  \caption{Found 4 Unique States}\label{fig:segment1}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_segment1.pdf}
+  \caption{Found 14 Unique States}\label{fig:segment2}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_segment2.pdf}
+  \caption{Found 13 Unique States}\label{fig:segment3}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_segment3.pdf}
+  \caption{Found 12 Unique States}\label{fig:segment4}
+  \end{subfigure}
+  \begin{subfigure}{1\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_full.pdf}
+  \caption{Initial state sequence seeded with states found in (a)--(d)}\label{fig:full}
+  \end{subfigure}
+  \caption{In (a--d), we show the state sequence resulting from 5 iterations
+  of the IHMM on each of the four quarters of the center-of-mass trajectory in
+  (e) after splitting it into 4 separate segments. We use the concatenation 
+  of the four state sequences as the initial sequence for the IHMM run on the 
+  fully trajectory in (e).
+  }\label{fig:seed_sequence}
   \end{figure}

### 2020-05-14 Ben_Manuscripts/hdphmm/Draft.tex
New supporting figures and mods to draft

@@
 \usepackage{xr}
+\usepackage{enumitem}
+\newcommand{\nclusters}{10}
 %\DeclareUnicodeCharacter{03C9}{$\omega$}
@@
   To cluster on $T_{ii}$, we first cast it in terms of the expected dwell times. The expected
-  value of the number of sequential self-transitions is simply $\frac{1}{1 - T_{ii}}$. This 
-  relationship correctly implies that dwell times approach infinity as $T_{ii}$ approaches
+  value of the number of sequential self-transitions is simply:
+  % BJC4: I numbered this equation because I reference it later.
+  \begin{equation}  
+   E[dwell time] = \frac{1}{1 - T_{ii}}
+   \label{eqn:dwell_times}
+  \end{equation}  
+  This relationship implies that dwell times approach infinity as $T_{ii}$ approaches
   1. Therefore we found the most success with agglomerative clustering by linearizing this
   relationship and clustering on $-\log(1 - T_{ii})$.
-  % (see Section~\ref{S-section:selfT_cluster} of the Supporting Information for a graphical illustration).
 
@@
 
-  \textit{Generating Stochastic IHMM Trajectory Realizations}: For each independent 
-  MD trajectory, we generated stochastic trajectory realizations using the finalized 
-  parameters of the associated IHMM. We drew state sequences with transition probabilities
-  given by $T$. While in a given state, we simulated motion according to the VAR(1) 
-  parameterization of that state. After each state transition, we set the unconditional
-  mean of the new state to the particle's position immediately before the state 
-  transition occurred.
-
-  \textit{Calculating MSD}: We quantified solute motion using the time averaged mean squared displacement (MSD)
-  of the solute center of mass trajectories.~\cite{meroz_toolbox_2015} The time-averaged MSD measures all observed
+  \textit{Generating Stochastic IHMM Trajectory Realizations}: We used two 
+  different methods to stochastically generate trajectories:
+  \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
+    \item For each independent MD trajectory, we generated stochastic trajectory
+    realizations using the finalized parameters of the associated IHMM. This 
+    results in 24 separate ensembles of trajectories for each solute studied. 
+    \item Using the clustered parameter sets, we generated a single ensemble
+	of trajectories. Realizations are representative of the combined behavior
+	of all solute trajectories.
+  \end{enumerate}
+
+  For both approaches, we drew state sequences with transition probabilities given 
+  by $T$ of the IHMM. While in a given state, we simulated motion according to the 
+  VAR(1) parameterization of that state. After each state transition, we set the 
+  unconditional mean of the new state to the particle's position immediately before
+  the state transition occurred.
+
+  \textit{Calculating mean squared displacement}: We quantified solute motion from
+  MD and from our stochastic trajectories using the time averaged mean squared 
+  displacement (MSD) of the axial ($z$) component of the solute center of mass
+  trajectories.~\cite{meroz_toolbox_2015} The time-averaged MSD measures all observed 
   displacements over time lag $\tau$:
@@
   \end{equation}
-  where T is the length of the trajectory. We reported $1 \sigma$ confidence intervals 
-  based on the results of 200 bootstrap trials. For each trail, we calculated the mean of 
-  $n$ random trajectories chosen with replacement from the pool of trajectories, where 
-  $n$ is the number of trajectories.
-
-  The MSD reported for each solute measured by our MD 
-  simulations is a distribution created from the 24 independent MSD curves. We predicted 
-  MSDs and their uncertainties with our stochastic models by bootstrapping the 
-  distribution of stochastically generated MSDs. For each bootstrap trial, we generated
-  24 independent trajectories using the 24 sets of IHMM parameters. We report the mean
-  and standard error of the bootstrapped MSD distributions.
+  where T is the length of the trajectory.
+
+  We reported the mean and $1 \sigma$ confidence intervals of the MSDs based on the 
+  results of 200 bootstrap trials. Our bootstrapping procedure varied dependent on the
+  method of trajectory generation:
+  \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
+  	\item For each trial, we generated 24 stochastic trajectories, one from each of
+  	the 24 independent IHMM models. The result of the bootstrap trial is the mean
+  	of the MSDs calculated from each trajectory. 
+    \item We generated an ensemble of 1000 independent stochastic trajectories using
+    the clustered parameter sets. For each trial, we calculated the MSD of 1000 
+    trajectories sampled, with replacement, from the ensemble.
+  \end{enumerate}
+
+  For MD trajectories, we bootstrapped according to Method 2.
+
+  \subsection{Predicting Selectivity}\label{method:selectivity}
+
+  In our previous work, we showed that in systems without convective flux, such
+  as our MD simulations, selectivity towards component $i$ over $j$ is simply:
+  \begin{equation}
+  S_{ij} = \frac{J_i / \Delta C_i}{J_j / \Delta C_j}
+  \label{eqn:selectivity_flux}
+  \end{equation}
+  where $J$ is solute flux and $\Delta C$ is the trans-membrane concentration
+  difference.~\cite{coscia_capturing_2020} The concentrations of solutes are the
+  same across our simulations, therefore Equation~\ref{eqn:selectivity_flux} 
+  reduces to the ratio of solute fluxes.
+
+  Solute flux, as written, can be expressed in terms of the product of solute 
+  diffusivity, $D_i$, within the membrane and a sorption coefficient, $K_i$, 
+  that quantifies the ability of the solute to move between the bulk solution
+  and and the membrane:
+  \begin{equation}
+    J_i = \frac{D_i K_i}{l}\Delta C
+  \end{equation}
+  where $l$ is the membrane thickness. For our purposes, $K_i$ and $l$ are 
+  irrelevant since we do not study pore entry effects or flux across finite
+  length pores. Therefore, in order to calculate selectivity, with respect
+  to quantities we can study with our MD simulations, it is only necessary that
+  we compare the ratio of diffusion constants:
+  \begin{equation}
+    S_{ij} = \frac{D_i}{D_j}
+    \label{eqn:selectivity_diffusivity}
+  \end{equation}
+  It can be shown on time scales where motion is uncorrelated, that the diffusion
+  constant is linearly proportional to the slope of the MSD curve:~\cite{einstein_investigations_1956}
+  \begin{equation}
+    \overline{z^2(\tau)} = 2 n D t
+    \label{eqn:msd_D}
+  \end{equation}
+  where $n$ is the number of spatial dimensions (1 in our case). Since the MSD
+  of our models enters a linear regime, we can estimate diffusion constants 
+  based on the slope of the linear region of the predicted MSD curves.
 
@@
 
-  We determined the number of hydrogen bonds between each solute and the membrane
-  as a function of time. Based on the geometric criteria of Luzar and Chandler, we 
-  define a hydrogen bond to exist if the distance between donor, D, and acceptor, 
-  A, atoms is less than 3.5\AA~and the angle formed by $D-H \cdots A$ is less than 
-  $30\degree$.~\cite{luzar_effect_1996}
-
-  We estimated the lifetime of hydrogen bonds by recording the length of 
-  sequential frames where solutes remained hydrogen bonded. We still counted sequences
-  where hydrogen bonds were broken for a single frame before reforming. Consistent
-  with our previous work, we reported the 95th percentile of hydrogen bond lifetimes
-  since their distribution is not Gaussian and to emphasize longer trapping periods.~\cite{coscia_chemically_2019}
-
-  We also measured the degree of association between solutes and sodium ions on a
-  frame-by-frame basis. We define a sodium ion to be associated with an atom if they
-  are within 2.5 \AA~of each other, as determined in our previous work.~\cite{coscia_chemically_2019}
+  \textit{Expected dwell times}:
+
+  \textit{Hydrogen bond detection}: We determined the number of hydrogen bonds 
+  between each solute and the membrane as a function of time. Based on the 
+  geometric criteria of Luzar and Chandler, we define a hydrogen bond to exist 
+  if the distance between donor, D, and acceptor, A, atoms is less than 
+  3.5\AA~and the angle formed by $D-H \cdots A$ is less than $30\degree$.~\cite{luzar_effect_1996}
+
+  \textit{Hydrogen bond lifetimes}: We estimated the lifetime of hydrogen bonds by 
+  recording the length of sequential frames where solutes remained hydrogen bonded.
+  We still counted sequences where hydrogen bonds were broken for a single frame 
+  before reforming. Consistent with our previous work, we reported the 95th 
+  percentile of hydrogen bond lifetimes since their distribution is not Gaussian
+  and to emphasize longer trapping periods.~\cite{coscia_chemically_2019}
+
+  \textit{Sodium ion association detection}: We also measured the degree of association
+  between solutes and sodium ions on a frame-by-frame basis. We define a sodium ion to
+  be associated with an atom if they are within 2.5 \AA~of each other, as determined 
+  in our previous work.~\cite{coscia_chemically_2019}
 
   %We developed a way to 
-  We measure the local density of the membrane at arbitrary
-  points in the unit cell as follows. We histogrammed the positions in three dimensions
-  Since our system is in a monoclinic unit cell, we periodically replicated
+  \textit{Local density measurements}: We measured the local density of the membrane at
+  arbitrary points in the unit cell as follows. We histogrammed the positions in three 
+  dimensions. Since our system is in a monoclinic unit cell, we periodically replicated
   the system in the $\pm x$, $y$ and $z$ directions and then chose the bounds on the
   histogram in order to create a rectangular box encompassing the unit cell with
-  a 1 nm buffer between the histogram and unit cell boundaries.~\cite{van_der_walt_numpy_2011} We then used a regular
-  grid interpolator in order to allow interpolation at arbitrary points within the grid.~\cite{virtanen_scipy_2020}
+  a 1 nm buffer between the histogram and unit cell boundaries.~\cite{van_der_walt_numpy_2011}
+  We then used a regular grid interpolator in order to allow interpolation at arbitrary
+  points within the grid.~\cite{virtanen_scipy_2020}
 
@@
   can produce trajectories that show qualitatively similar hopping and trapping 
-  behavior to the MD trajectories. It is important that our model reproduces this 
-  behavior so that we can have confidence in its usefulness for quantitative 
-  predictions.
+  behavior to the MD trajectories to which they were fit. It is important that our
+  model reproduces this behavior so that we can have confidence in its usefulness
+  for quantitative predictions.
 
@@
   \includegraphics[width=\textwidth]{qualitative_unclustered_MET2.pdf}
-  \caption{We can generate trajectories which bear qualitative resemblance to
-  the MD trajectories. Solute trajectories generated by the IHMM (blue) show
-  the same hopping and trapping behavior exhibited by MD (black).
+  \caption{We can use realizations of the IHMM to generate trajectories which 
+  bear qualitative resemblance to the MD trajectories. We used the parameters 
+  of the IHMM, whose state segments are visualized in 
+  Figure~\ref{fig:rz_unclustered}, in order to construct an ensemble of 
+  characteristic trajectories. Solute trajectories generated with
+  the IHMM (blue) show the same hopping and trapping behavior exhibited by 
+  MD (black).
   }\label{fig:qualitative_unclustered}
@@
 
-  \textit{Deviations of the IHMM from Molecular Motion}: From a quantitative
-  standpoint, using the IHMM as a predictive tool has two 
-  shortcomings. First, in many cases, the MSD predicted by realizations of the 
-  IHMM under-predicts that of MD (see Figure~\ref{fig:unclustered_msds}).
-  Second, the shapes of the MSD curves at short time lags are very different.
+  In Figure~\ref{fig:unclustered_msds}, we show that we can reproduce the 
+  MD MSDs on long timescales within uncertainty using realizations of the 
+  IHMM.
+  \begin{itemize}
+    \item We generated the MSD curves using Method 1 described in 
+    Section~\ref{method:realizations} of the methods.
+    \item Our ability to reproduce these curves gives use confidence
+    in their long term predictions.
+  \end{itemize}
 
@@
 
-  The IHMM under-predicts the MD MSD due to its tendency to favor fewer states. 
-  Disjoint segments with similar VAR parameters, but different lengths of entrapment
-  can be parameterized as the same state. In Figure~\ref{fig:dwell_distributions}, 
-  we compare the overall dwell time distributions generated directly from MD simulations to that 
-  generated from realizations of the IHMM. We do this by measuring the time spent in 
-  each independent same-state segment. Some of the probability density of short 
-  trapping times in the MD simulations gets shifted to medium length trapping times
-  in realizations of the IHMM. In Figure~\ref{fig:dwell_distributions_modT} 
-  and~\ref{fig:msd_modT}, we show that by modifying the transition matrix to 
-  encourage transitions towards states with shorter dwell times, we can more closely
-  reproduce the dwell time distribution and MSD of MD. This is because most solute
-  motion is a consequence of transitions between trapped states.
-
-  % BJC4: A lower priority supporting information section I've had in mind is one
-  % with tips for fitting and validating the IHMM on individual trajectories.  
-%  In many cases, especially evident where MSD predictions over-estimate MD, there
-%  is some error in the state sequence segmentation. In Section~\ref{S-section:fitting_tips}
-%  of the Supporting Information, we give some tips based on our experience of how to 
-%  initialize IHMM fits in order to reduce error.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{dwell_distributions.pdf}
-  \caption{}\label{fig:dwell_distributions}
-  \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{dwell_distributions_modT.pdf}
-  \caption{}\label{fig:dwell_distributions_modT}
-  \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{unclustered_msd_MET_modT.pdf}
-  \caption{}\label{fig:msd_modT}
-  \end{subfigure}
-  \caption{(a) The density of short dwell times compiled from realizations of
-  the IHMM fit to methanol trajectories is below that measured directly from 
-  the MD trajectories. If we modify the transition matrix in order to favor 
-  transitions towards states with short dwell times, we can more closely match
-  the (b) dwell time distributions and (c) MSDs.}\label{fig:slow_T}
-  \end{figure}
-
-  At extremely short time lags, the MSD is generally over-predicted by the IHMM
-  (see Figure~\ref{fig:unclustered_msd_shortlag}) because the VAR(1) model assumes
-  multivariate Gaussian noise while the MD data suggests the noise is better 
-  modeled by more general L\'evy stable noise. The first time lag of the MSD is
-  equivalent to the variance of all observed fluctuations (first-order difference). 
-  The IHMM simulation appears to over-estimate the variance because the actual 
-  distribution of solute fluctuations has heavy tails with a smaller variance. (Figure~\ref{fig:emission_widths}).
-  The total distribution of hops is expected to be heavy tailed because it is a
-  combination of hop distributions from many states with different variances. More
-  interestingly, in Figure ~\ref{fig:state_emission_widths}, we show that the 
-  emission distribution of a single state picked out by the IHMM is fit better by
-  a more general L\'evy distribution while the emissions from IHMM realizations are
-  Gaussian, as expected. An improvement to the IHMM that may allow dynamics more 
-  faithful to MD would use an autoregressive model with L\'evy stable noise. However,
-  this would be less computationally efficient due to lack of conjugate priors.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{unclustered_msd_MET_shortlag.pdf}
-  \caption{}\label{fig:unclustered_msd_shortlag}
-  \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{emission_widths.pdf}
-  \caption{}\label{fig:emission_widths}
-  \end{subfigure}
-  \begin{subfigure}{0.32\textwidth}
-  \includegraphics[width=\textwidth]{state_emission_widths.pdf}
-  \caption{}\label{fig:state_emission_widths}
-  \end{subfigure}
-  \caption{(a) At short time lags, the MD MSD (black) and the IHMM MSD (orange)
-  differ significantly in their shape and curvature. (b) While the 
-  fluctuations in $z$ of both distributions are heavy-tailed, fitting well to zero-centered
-  symmetric L\'evy stable distributions with stability parameters, $\alpha$, the IHMM has
-  a wider variance. (c) The distribution of fluctuations in a chosen state frequently
-  visited by methanol is heavy tailed, but the IHMM is constrained to produce fluctuations
-  from a multivariate normal distribution ($\alpha$=2 in each dimension).
-  }\label{fig:short_timelags}
-  \end{figure}
-
-  Also apparent from Figure~\ref{fig:unclustered_msd_shortlag} is that the 
-  curvature of the MD MSD is far more gradual than that generated by the IHMM.
-  This is because the VAR(1) model is only correlated to its previous fluctuation
-  while the MD simulations suggest that correlation persists for at least tens
-  of nanoseconds.
-    % BJC2: could probably use a correlation function to suggest the AR order and stick the plot in SI
-  One may be able to reproduce the curvature at short time lags with higher order
-  VAR models, but it becomes a much higher dimensional parameterization that would
-  require significantly more data in order to produce stable results. Since we 
-  are interested in reproducing longer time scale behavior, it is not an issue of
-  great concern.
-
-  % BJC2: I'm not sure if the width of the hop length distribution has a significant 
-  % effect on average MSD, since it's symmetric. Something to test next week.
-
   \subsection{Using IHMM Parameters to Predict Selectivity}\label{section:macroscopic_properties}
 
-  % BJC2: I think it makes sense to talk about selectivity here, but I'm not sure 
-  % the best way to go about it.
-
-  Keeping in mind the the shortcomings of the IHMM, we can now propagate realizations onto long 
-  time scales in order to predict solute flux and thus selectivity. 
-  \begin{itemize}
-    \item In our previous work, we showed that in systems without convective flux, selectivity is
-    simply the ratio of solute fluxes.
-%    \item Although the magnitude of our MSD predictions are typically below those of
-%    MD, we may still obtain reasonable estimates of selectivity.
-  \end{itemize}
-
-  We can use the ratio of solute fluxes predicted by realizations of our models in order to 
-  estimate selectivity.
-  \begin{itemize}
-    \item Exact methodology under development
-    \item Will probably just take advantage of long timescale MSD linearity in order to get
-    flux, rather than mean first passage time approach.
-    \item Need to figure out how to deal with differences in MSD under-estimates
-  \end{itemize}
+  Since we can generate trajectories that share features similar to MD simulations, 
+  it is now reasonable to project solute behavior onto much longer time scales.
+  \begin{itemize}
+    \item The IHMM MSD predictions quickly enter a linear regime, therefore we can 
+    project long timescale MSDs based on the predicted diffusion constant as described
+    in Section~\ref{method:selectivity}.
+  \end{itemize}
+
+  %BJC4: figure here
+
+  %BJC4: some kind of brief selectivity analysis here
 
@@
 
-  \subsubsection*{State Clustering}
-
-  In order to reduce the state space to a more manageable size, and to allow
-  different solute trajectories to share similar behavior, we clustered the
-  states identified by the IHMM for each solute as described in 
-  Section~\ref{method:clustering}. In Figure~\ref{fig:mechanism_map}, we show
-  the results of clustering on the same trajectory from 
-  Figure~\ref{fig:rz_unclustered}. We chose to use X clusters based on the
-  criteria described in Section~\ref{method:clustering}. Therefore, we reduced 
-  the total state space from 300 to X. By working to understand the parameters
-  of each cluster, we can gain an understanding of associated solute transport
-  mechanisms responsible for those parameters.
-
-  \subsubsection*{Relating Clusters to Mechanisms}
-
-  The parameters of each cluster can be related to dominant solute-membrane interactions.
-  \begin{itemize}
-    \item Based on our previous work, we know that hydrogen bonding, sodium ion 
-    association and radial location within the membrane pores will have a significant
-    influence on transport properties. 
-    \item Even without our previous work, it would still be easy to speculate that these 
-    interactions might occur and could therefore be used to help understand the 
-    states identified by the IHMM.
-    \item We have also incorporated membrane density as a physical metric because we 
-    know the membrane has an inhomogeneous structure.
-  \end{itemize}
-
-  \textit{Learning from individual trajectories}: In Figure~\ref{fig:mechanism_map}, 
-  we demonstrate the wide range of behavior exhibited by a representative 2D methanol
-  trajectory.
-%BJC2: reducing duplication
-%  The coordinates
-%  are colored according to the cluster with which methanol's dynamics are most consistent,
-%  which implies that this particular methanol trajectory exhibits eight distinct dynamical 
-%  behaviors (in order of their first appearance, they are colored dark yellow, red, light
-%  blue, light green, orange, blue, teal and lime green).
-  The solute time series are coupled with color coded bars which describe the solute's
-  local environment and physical interactions that it undergoes at each trajectory frame. 
-%  From the top, they describe 
-%  whether the solute is associated with sodium, whether the solute is hydrogen bonding
-%  with the monomer as well as to what part of the monomer it is hydrogen bonding, and 
-%  finally, the local number density surrounding the solute.
-
-  %BJC2: the exact figure will change, but most of what I say shouldn't
+  \textit{State Clustering}: In order to reduce the state space to a more 
+  manageable size, and to allow different solute trajectories to share 
+  similar behavior, we clustered the states identified by the IHMM for each
+  solute as described in Section~\ref{method:clustering}. In 
+  Figure~\ref{fig:clustered_traj_MET}, we show the results of clustering on the 
+  same methanol trajectory from Figure~\ref{fig:rz_unclustered}. Based on 
+  the criteria described in Section~\ref{method:clustering},
+  we chose to reducing the total state space for methanol from 287 to \nclusters.
+
+  Our goal is to derive the simplest model which adequately distinguishes
+  different types of solute motion. By working to understand the parameters of 
+  each cluster, we can uncover the associated transport mechanisms responsible
+  for those parameters.
+
   \begin{figure}
   \centering
-  \begin{subfigure}{0.75\textwidth}
-  \includegraphics[width=\textwidth]{mechanism_map.png}
-  \caption{}
-  \end{subfigure}
-  \begin{subfigure}{0.24\textwidth}
-  \includegraphics[width=\textwidth]{monomer_oxygens.png}
-  \caption{}
-  \end{subfigure}
-  %MRS: a lot of this caption test is duplicated from the main text. I would suggest reducing the duplication.
-  %BJC: you think better to have more detail in text or in caption?
-  %MRS2: at a certain point, it should be in the text.  In the caption, I would just state what the point of the plot is, 
-  % and define the colors/data/etc.  But full explanation would be better in the text. Captions should be scannable quickly,
-  % based on how people process papers, and this should be significantly shorter for readability. 
- \caption{(a) We can learn a significant amount of detail about solute motion by viewing 
-  solute trajectories color-coded according to their clustered dynamical behavior alongside
-  plots of the dominant molecular interactions and descriptions of the membrane's local 
-  environment. In the plot above, we show the radial and axial coordinates of a single
-  methanol molecule over the course of the equilibrated portion of its MD simulation.
-  Disjoint segments of the same color imply the solute behaves similarly at different 
-  points of the trajectory because their VAR parameters place them in the same cluster. 
-  There are eight distinct dynamical modes exhibited by this trajectory. In order
-  of their first appearance, they are colored dark yellow, red, light blue, light green,
-  orange, blue, teal and lime green. On the top of the plot are bars which represent different
-  physical interactions and the membrane's local environment as a function of time. The top 
-  bar is colored green at time points where solutes are associated with sodium. Methanol 
-  associates with sodium ions relatively infrequently. The next bar down is colored when hydrogen
-  bonds exist. The colors match the enlarged oxygen atoms highlighted in (b). Blue slivers
-  correspond to hydrogen bonds donated to the monomer's carboxylate head group. Green slivers
-  correspond to  hydrogen bonds donated to the ether linkages between the head groups
-  and tails. Red slivers correspond to hydrogen bonds donated to the oxygens on the ends
-  of the monomer tails. Methanol exhibits significant hydrogen bonding with all parts of
-  the monomer. Which part of the monomer methanol hydrogen bonds to is heavily correlated
-  to the solute's $r$ coordinate. Finally, the bar with the blue gradient represents the local 
-  membrane density based on the solute's ($r$, $z$) coordinate. Darker shades of blue
-  correspond to higher membrane densities. The density appears to be higher when methanol
-  motion is restricted (e.g. from 75 to 550 ns). It is relatively low in areas where methanol's
-  position fluctuates significantly (e.g. from 550 to 700 ns). 
-  }\label{fig:mechanism_map}
+  \includegraphics[width=\textwidth]{clustered_traj_MET_ward_10.pdf}
+  \caption{We reduced the total state space from 287 to 10 total states 
+  shared across all trajectories. For the trajectory in this figure, we reduced
+  the total number of states from 24 (see Figure~\ref{fig:rz_unclustered}) to
+  5.}\label{fig:clustered_traj_MET}
   \end{figure}
 
-  %MRS2: suggest subsubcaptions/italics at the start of parentheses to make it easier for a reader to see the structure.
-  %MRS2: like \textit{hydrogen bonding patterns}: etc.
-
-  One can gain useful chemical intuition just by studying plots like 
-  Figure~\ref{fig:mechanism_map}. It is clear that, for methanol, association 
-  with sodium is a much rarer interaction than hydrogen bonding with the 
-  LLC monomers. Methanol hydrogen bonds to all regions of the monomers dependent
-  on its radial position. Its fluctuations tend to be smallest when hydrogen bonded
-  or in areas of high local number density. For example, from approximately 75 to 
-  525 ns, methanol appears to be trapped in a high density region of the tails.
-  In the time that follows, it enters a region of relatively low density where 
-  fluctuations are quite large. During this time period, there is intermittent, 
-  short-lived hydrogen bonding with the oxygen atoms at the tail ends, as suggested
-  by the frequent state changes during that time period and red slivers in the bar
-  above. Significant hops in the $z$ direction appear to be described by the dark blue
-  state. After entering the dark blue state ca. 850 ns, methanol appears to jump
-  significantly in the $z$ direction from a hydrogen bonded state with the ether 
-  linkages to a hydrogen bonded state with a head group in a monomer below it.
-
-  %MRS2: not entirely clear about the purpose of this paragraph? Seems to be just saying it's possible to learn more?
-  %MRS2: should clarify.
-  %BJC3: It was meant to be transitory but can probably cut out with the addition of the subsection title
-%  It is clear that there is a wealth of information in these plots, but they don't give
-%  the complete picture needed in order to formulate LLC membrane design principles. One
-%  can analyze each segment sequentially and form a clear picture of this instance of 
-%  methanol's behavior without the need to visualize the trajectory with software like VMD.~\cite{humphrey_vmd:_1996}
-%  However, it is still possible to gain a more general understanding of methanol's average
-%  behavior.
+  \textit{Dynamics of clustered parameter sets}: The clustered parameter sets
+  allow transitions between dynamics exhibited by the same solute from independent 
+  trajectories. This allows us to create hybrid trajectories which draw on all
+  solute behavior.
+
+  Realizations based on the 10 clustered parameter sets do not show the same
+  qualitative dynamics as the MD simulation trajectories. 
+  \begin{itemize}  
+    \item In Figure~\ref{fig:qualitative_clustered_MET}, we compare MD 
+    trajectories to realizations of our model using the clustered parameter sets.
+    \item They lack the diversity of behavior which we see in the MD simulation trajectories.
+    \item They do not show the same range of trapping times and hop lengths.
+    \item If we use a higher number of clusters, the qualitative match improves, but
+    at the cost of a larger state space to interpret (see Figure~\ref{S-fig:qualitative_improvement}
+    of the Supporting Information).
+  \end{itemize}
+
+  In addition to qualitative mismatches, realizations of the clustered IHMM 
+  under-predict the unclustered MSD predictions and the MD MSD. 
+  \begin{itemize}
+    \item Much of a solute's MSD is likely a consequence of short-lived trapping states
+    with high variances.
+    \item When clustering, disjoint segments with similar enough parameters are
+    re-parameterized together as part of the same state, lengthening the lifetimes 
+    of very short-lived states and suppressing the fluctuations of high variance states.
+    \item In Figure~\ref{fig:clustered_MSD}, it is evident that increasing the number
+    of clusters increases the predicted MSD.
+    \item Matching the unclustered MSDs would likely require many more clusters, at 
+    which point the benefits of clustering are lost. 
+    %BJC: I don't think the following discussion is necessary anymore.
+%    \item In Figure~\ref{fig:dwell_distributions}, we compare the overall dwell time
+%    distributions generated directly from MD simulations to that generated from 
+%    realizations of the IHMM. 
+%    \item We do this by measuring the time spent in each independent same-state segment.
+%    \item Some of the probability density of short trapping times in the MD simulations 
+%    gets shifted to medium length trapping times in realizations of the IHMM. 
+%    \item In Figure~\ref{fig:dwell_distributions_modT} and~\ref{fig:msd_modT}, we show 
+%    that by modifying the transition matrix to encourage transitions towards states with
+%    shorter dwell times, we can more closely reproduce the dwell time distribution and 
+%    MSD of MD. This is because most solute motion is a consequence of transitions between
+%    trapped states.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.63\textwidth}
+  \includegraphics[width=\textwidth]{qualitative_clustered_MET_10.pdf}
+  \caption{}\label{fig:qualitative_clustered_MET}
+  \end{subfigure}
+  \begin{subfigure}{0.35\textwidth}
+  \vspace{2.25em}
+  \includegraphics[width=\textwidth]{msd_nclusters.pdf}
+  \caption{}\label{fig:clustered_MSD}
+  \end{subfigure}
+  \caption{(a) Stochastic trajectory realizations generated from our model (blue) based on
+  the clustered methanol parameters do not qualit}\label{fig:clustered_dynamics}
+  \end{figure}
+
+%  \begin{figure}
+%  \centering
+%  % BJC4: combine (a) and (b). Add figure with MSD prediction
+%  \begin{subfigure}{0.32\textwidth}
+%  \includegraphics[width=\textwidth]{dwell_distributions.pdf}
+%  \caption{}\label{fig:dwell_distributions}
+%  \end{subfigure}
+%  \begin{subfigure}{0.32\textwidth}
+%  \includegraphics[width=\textwidth]{dwell_distributions_modT.pdf}
+%  \caption{}\label{fig:dwell_distributions_modT}
+%  \end{subfigure}
+%  \begin{subfigure}{0.32\textwidth}
+%  \includegraphics[width=\textwidth]{unclustered_msd_MET_modT.pdf}
+%  \caption{}\label{fig:msd_modT}
+%  \end{subfigure}
+%  \caption{(a) The density of short dwell times compiled from realizations of
+%  the IHMM fit to methanol trajectories is below that measured directly from 
+%  the MD trajectories. If we modify the transition matrix in order to favor 
+%  transitions towards states with short dwell times, we can more closely match
+%  the (b) dwell time distributions and (c) MSDs.}\label{fig:slow_T}
+%  \end{figure}
+
+% BJC: probably a bad idea
+%  It may still be possible to use these hybrid trajectories in order to predict
+%  selectivity since they undershoot the MD MSD by a consistent number and 
+%  the ratios will stay the same.
 
@@
   % can still use this framework to study mechanisms.
-  \textit{Learning from all trajectories}: We may learn the most by studying the
-  dynamical modes common to the majority of 
-  the solute trajectories. Using the IHMM, we identified 33 total dynamical modes 
-  exhibited by methanol. Of those, only six states appear in a third (8 out of 24) 
-  or more methanol trajectories, and three of them appear in over 50 \% of the 
-  methanol trajectories. 12 of the detected states are shared by two or less 
-  methanol trajectories. In Figure~\ref{fig:common_states_MET_lines}, we plot 
-  representative dynamics of each of the six states which we determined to be prevalent.
-  We also chose to study a seventh state, which only appears in three out of
-  24 trajectories, because methanol experiences very long periods of entrapment
-  while in this state. Long trapping events, even if they are relatively rare, will
-  have a significant influence on solute flux. No trajectory contains all seven states.
-  However, the trajectory in Figure~\ref{fig:mechanism_map} exhibits all modes except
-  states 6 and 7. The states in Figure~\ref{fig:common_states_MET} are colored to match
-  states that also appear in Figure~\ref{fig:mechanism_map}.
-
-  %BJC2: Again, this will change, but will follow the same general flow
-  We can begin to dissect the dynamics of each state by studying their parameters.
-  States 1, 3 and 5 have radial means near 1 nm or less (see y axis of $r$ direction 
-  plot in Figure~\ref{fig:common_states_MET_lines}), which suggest that they occur
-  close to the pore centers. States 2, 4, 6 and 7 occur well within the tail region
-  of the membrane. States 1 and 2 have higher covariances in both the axial and radial
-  directions compared to all other states. Covariance in each dimension appears to have
-  a strong correlation. States 3 and 5 (in the pore region) as well as states 4, 6 and
-  7 (in the tail region) are primarily distinguished based on their autoregressive 
-  coefficients, A. Higher values of A generally lead to more wandering about the state
-  mean. One could argue that the parameters of states 3--7 are actually very close which
-  suggests that solutes might behave alike in morphologically distinct regions of the 
-  membrane.
-
-  Despite some similarity in their VAR parameters, the length of time spent in states 
-  3--7 appears to be dependent on the solute's radial location. Based on the 
-  self-transition probabilities, we estimated the average time spent by each solute in
-  each state (Figure~\ref{fig:dwell_times_MET}). States 3, 5 and 7 have long dwell times
-  relative to the rest because they have high self-transition probabilities. Somewhat 
-  surprisingly, both states 3 and 5 correspond to solutes located close to a pore center,
-  where one might expect solute motion to be less restricted. Although solutes in states
-  4 and 6 are in the viscous tail region, their dwell times are only intermediate. This
-  could be due to inhomogeneity in the tail region which causes transitions between many
-  different trapped states but with little net effect on solute MSD. However, there are
-  instances of states within the tail region with dwell times that exceed 100--200 ns,
-  as shown by our inclusion of state 7. There are no other states with dwell times longer
-  than state 5 in the pore region.
-
-  States 1 and 2 exhibit the shortest dwell times of the states studied. This is 
-  consistent with the trajectory in Figure~\ref{fig:mechanism_map}. State 2 is the 
-  shortest lived state, appearing to bridge other tail region states. State 1 
-  appears to represent a significant hopping state. It has a high covariance and
-  occurs near the pore center, where there is less obstruction to solute motion.
-  It's dwell time of ca.~8 ns, suggests that solutes stay in this highly mobile 
-  state for long enough for their positions to displace significantly.
+
+%  \subsubsection*{Relating Clusters to Mechanisms}
+%  
+%  The parameters of each cluster can be related to dominant solute-membrane interactions.
+%  \begin{itemize}
+%    \item Based on our previous work, we know that hydrogen bonding, sodium ion 
+%    association and radial location within the membrane pores will have a significant
+%    influence on transport properties. 
+%    \item Even without our previous work, it would still be easy to speculate that these 
+%    interactions might occur and could therefore be used to help understand the 
+%    states identified by the IHMM.
+%    \item We have also incorporated membrane density as a physical metric because we 
+%    know the membrane has an inhomogeneous structure.
+%  \end{itemize}
+
+%  \textit{Learning from individual trajectories}: In Figure~\ref{fig:mechanism_map}, 
+%  we demonstrate the wide range of behavior exhibited by a representative 2D methanol
+%  trajectory.
+%%BJC2: reducing duplication
+%%  The coordinates
+%%  are colored according to the cluster with which methanol's dynamics are most consistent,
+%%  which implies that this particular methanol trajectory exhibits eight distinct dynamical 
+%%  behaviors (in order of their first appearance, they are colored dark yellow, red, light
+%%  blue, light green, orange, blue, teal and lime green).
+%  The solute time series are coupled with color coded bars which describe the solute's
+%  local environment and physical interactions that it undergoes at each trajectory frame. 
+%%  From the top, they describe 
+%%  whether the solute is associated with sodium, whether the solute is hydrogen bonding
+%%  with the monomer as well as to what part of the monomer it is hydrogen bonding, and 
+%%  finally, the local number density surrounding the solute. 
+%
+%  %BJC2: the exact figure will change, but most of what I say shouldn't
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.75\textwidth}
+%  \includegraphics[width=\textwidth]{mechanism_map.png}
+%  \caption{}
+%  \end{subfigure}
+%  \begin{subfigure}{0.24\textwidth}
+%  \includegraphics[width=\textwidth]{monomer_oxygens.png}
+%  \caption{}
+%  \end{subfigure}
+%  %MRS: a lot of this caption test is duplicated from the main text. I would suggest reducing the duplication.
+%  %BJC: you think better to have more detail in text or in caption?
+%  %MRS2: at a certain point, it should be in the text.  In the caption, I would just state what the point of the plot is, 
+%  % and define the colors/data/etc.  But full explanation would be better in the text. Captions should be scannable quickly,
+%  % based on how people process papers, and this should be significantly shorter for readability. 
+% \caption{(a) We can learn a significant amount of detail about solute motion by viewing 
+%  solute trajectories color-coded according to their clustered dynamical behavior alongside
+%  plots of the dominant molecular interactions and descriptions of the membrane's local 
+%  environment. In the plot above, we show the radial and axial coordinates of a single
+%  methanol molecule over the course of the equilibrated portion of its MD simulation.
+%  Disjoint segments of the same color imply the solute behaves similarly at different 
+%  points of the trajectory because their VAR parameters place them in the same cluster. 
+%  There are eight distinct dynamical modes exhibited by this trajectory. In order
+%  of their first appearance, they are colored dark yellow, red, light blue, light green,
+%  orange, blue, teal and lime green. On the top of the plot are bars which represent different
+%  physical interactions and the membrane's local environment as a function of time. The top 
+%  bar is colored green at time points where solutes are associated with sodium. Methanol 
+%  associates with sodium ions relatively infrequently. The next bar down is colored when hydrogen
+%  bonds exist. The colors match the enlarged oxygen atoms highlighted in (b). Blue slivers
+%  correspond to hydrogen bonds donated to the monomer's carboxylate head group. Green slivers
+%  correspond to  hydrogen bonds donated to the ether linkages between the head groups
+%  and tails. Red slivers correspond to hydrogen bonds donated to the oxygens on the ends
+%  of the monomer tails. Methanol exhibits significant hydrogen bonding with all parts of
+%  the monomer. Which part of the monomer methanol hydrogen bonds to is heavily correlated
+%  to the solute's $r$ coordinate. Finally, the bar with the blue gradient represents the local 
+%  membrane density based on the solute's ($r$, $z$) coordinate. Darker shades of blue
+%  correspond to higher membrane densities. The density appears to be higher when methanol
+%  motion is restricted (e.g. from 75 to 550 ns). It is relatively low in areas where methanol's
+%  position fluctuates significantly (e.g. from 550 to 700 ns). 
+%  }\label{fig:mechanism_map}
+%  \end{figure}
+%
+%  One can gain useful chemical intuition just by studying plots like 
+%  Figure~\ref{fig:mechanism_map}. It is clear that, for methanol, association 
+%  with sodium is a much rarer interaction than hydrogen bonding with the 
+%  LLC monomers. Methanol hydrogen bonds to all regions of the monomers dependent
+%  on its radial position. Its fluctuations tend to be smallest when hydrogen bonded
+%  or in areas of high local number density. For example, from approximately 75 to 
+%  525 ns, methanol appears to be trapped in a high density region of the tails.
+%  In the time that follows, it enters a region of relatively low density where 
+%  fluctuations are quite large. During this time period, there is intermittent, 
+%  short-lived hydrogen bonding with the oxygen atoms at the tail ends, as suggested
+%  by the frequent state changes during that time period and red slivers in the bar
+%  above. Significant hops in the $z$ direction appear to be described by the dark blue
+%  state. After entering the dark blue state ca. 850 ns, methanol appears to jump
+%  significantly in the $z$ direction from a hydrogen bonded state with the ether 
+%  linkages to a hydrogen bonded state with a head group in a monomer below it.
+
+  \textit{The dynamics of frequently occurring states}: We may learn the most by 
+  studying the dynamical modes common to the majority of the solute trajectories.
+  \begin{itemize}
+  	\item Of the 10 state clusters, only 5 appear in a significant number of 
+  	solute trajectories (Figure~\ref{fig:prevalence}).
+  	\item Although a majority of the solutes visit these 5 states the
+  	amount of time spent in each varies widely. 
+  \end{itemize}
 
@@
   \centering
-  \begin{subfigure}{0.6\textwidth}
-  \includegraphics[width=\textwidth]{common_states_MET.pdf}
-  \caption{}\label{fig:common_states_MET_lines}
-  \end{subfigure}
-  \begin{subfigure}{0.35\textwidth}
-  \includegraphics[width=\textwidth]{A_sigma_scatter_MET.pdf}
-  \caption{}\label{fig:A_sigma_scatter_MET}
-  \includegraphics[width=\textwidth]{dwell_times_MET.pdf}  % No errorbars because these are expected values
-  \caption{}\label{fig:dwell_times_MET}
-  \end{subfigure}
-  %MRS: a lot of text here in the caption - think about reducing duplication with the text, and moving some to the text.
-  %BJC2: will rework once final plots are made.
-  \caption{We can learn the most about methanol's behavior by studying the dynamics
-  of the states common to many of the methanol trajectories. In (a), we show representative
-  dynamics of six states that are common to more than one third of the solute trajectories. 
+  \includegraphics[width=0.5\textwidth]{prevalence.pdf}
+  \caption{5 out of the 10 clustered states are visited by 15 or more of the solute
+  trajecotries. The solutes spend varying amounts of time in each of these states.
+  }
+  \label{fig:prevalence}
+  \end{figure}
+
+  We can begin to hypothesize mechanisms by studying the behaviors defined by the 
+  state parameters.
+  \begin{itemize}
+  	\item In Figure~\ref{fig:common_states_lines}, we plot representative 
+  	dynamics of each of the five most visited states.
+  	\item The states exhibit a range of autoregressive and trapping behavior
+  	throughout the membrane pores.
+%  	\item There is good representation by states across a range of radial distances
+%  	from the pore centers. 
+  \end{itemize}
+
+  Since the radial means are weighted averages of the states used to parameterize
+  each cluster, for interpretive purposes, it is important to recognize that the means
+  only provide clues towards the general location of the solute. 
+  \begin{itemize}
+  	\item For example, the radial mean of state 3 is 1.4 nm from the pore center. 
+  	\item However, inspection of Figure~\ref{fig:clustered_traj_MET} suggests that this 
+  	type of behavior actually occurs radially throughout the pore.
+  	\item There are instances of state 3 less than 1 nm from the pore center and more 
+  	than 2 nm from the pore center. 
+  	\item In this case, the radial mean only suggests that this type of behavior 
+  	happens in both regions somewhat equally.
+  \end{itemize}
+
+  Solutes exhibit a range of autoregressive behavior as shown by the representative 
+  solute trajectories in Figure~\ref{fig:common_states_lines} and the scatter
+  plot in Figure~\ref{fig:A_sigma_scatter}.
+  \begin{itemize}
+  	\item In most cases, the eigenvalues of $A$ and $\Sigma$ appear nearly paired
+  	in their radial and axial dimensions, which implies nearly symmetric behavior 
+  	with off-diagonals both matrices near zero.
+  	\item The most notable exception is state 3, which has a much higher radial 
+  	eigenvalue of the covariance matrix.
+  	\item Both eigenvalues are actually of state 3's covariance are actually quite
+  	large. This implies relatively large fluctuations in the $z$ direction and even
+  	bigger fluctuations in the $r$ direction.
+  	\item All states have slightly lower covariance in the axial direction. It's
+  	likely easier for solutes to move laterally rather than to move up through the
+  	alkane chains.
+  	\item States 3 and 4 show a strong previous-hop dependence (high $A$) while
+  	the rest of the states have a somewhat weaker dependence.
+  \end{itemize}
+
+  Solutes are trapped for various lengths of time.
+  \begin{itemize}
+    \item On average, state 4 has the longest dwell times and state 3 has
+    the shortest dwell times while the rest have intermediate dwell times.
+    \item This is partially confirmed via inspection of Figure~\ref{fig:clustered_traj_MET},
+    however. 
+    \item Once again, since we clustered, it is important to avoid distraction
+    by the exact dwell time values, and to focus on their relative magnitudes
+  \end{itemize}
+
+  % BJC4: Not sure if this is useful. Maybe can replace above three paragraphs 
+  % with this. Helps us look for mechanisms.
+  By studying the parameters, it is now easier to describe the state behavior.
+  \begin{enumerate}[label={State \theenumi :}, leftmargin=3.5\parindent]
+     \item This state has intermediate dwell times with high past-hop dependence.
+     The radial mean and evidence from Figure~\ref{fig:clustered_traj_MET} suggests
+     that this state is common in the tail and pore region.
+     \item This state seems to occur exclusively in the tail region based on its radial
+     mean. Its fluctuations are small and there is little past hop dependence
+     \item This is likely a hopping state that strongly contribute to the solute's MSD. 
+     It is short lived and takes very large hops. This type of behavior is exhibited 
+     near and far from the pore center as discussed earlier.
+     \item This is a trapping state with a strong dependence on its previous fluctuation.
+     Evidence from Figure~\ref{fig:clustered_traj_MET} and a radial mean of 1.8 suggest
+     that it tends to occur at intermediate distances from the pore center.
+     \item This is an intermediate-length trapping state that occurs close to the pore
+     center. It's fluctuations are tight and relatively independent of its previous 
+     fluctuation.
+  \end{enumerate}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.58\textwidth}
+  \includegraphics[width=\textwidth]{common_states.pdf}
+  \caption{}\label{fig:common_states_lines}
+  \end{subfigure}
+  \begin{subfigure}{0.41\textwidth}
+  \includegraphics[width=\textwidth]{A_sigma_scatter.pdf}
+  \caption{}\label{fig:A_sigma_scatter}
+  \includegraphics[width=\textwidth]{dwell_times.pdf}
+  \caption{}\label{fig:dwell_times}
+  \end{subfigure}
+  \caption{The 5 most visited states by methanol show a range of dynamical behavior. In 
+  (a), we show representative dynamics of these states. All time series have a mean of zero and are
+  shifted to put the mean in line with the $y$-axis labels for the purpose of visualizing them.
   The $y$-axis labels of the $r$ coordinate plot specify the radial mean of each clustered 
-  state. The percentage of trajectories in which the states appear are labeled to the right of
-  the $r$ plots. States 1--5 appear in the trajectory shown in Figure~\ref{fig:mechanism_map}
-  and are colored to match for easy visual comparison. All time series have a mean of zero and are
-  shifted to put the mean in line with the $y$-axis labels for the purpose of visualizing them. 
+  state. All of the states pictured appear in the trajectory shown in 
+  Figure~\ref{fig:clustered_traj_MET} and are colored to match.
   (b) We can begin to understand the solute behaviors demonstrated in (a) by understanding their VAR 
-  parameters. States 1 and 2 have higher covariances in both the axial and radial directions compared
-  to all other states. This should lead to significant solute displacement. Covariance in each dimension
-  appears to have a strong correlation. 
-  %MRS2: correlation with what?
-  States 3--6 all have relatively low covariances, which may
-  be characteristic of trapped states. They are primarily distinguished based on the magnitude of their 
-  autoregressive coefficients, A, and radial means. Higher values of A imply motion which wanders 
-  more about the mean. States 1, 3 and 5 have radial means near 1 nm or less, which suggest that they
-  occur close to the pore centers. States 2, 4 and 6 occur well within the tail region of the membrane.
-  (c) Using the transition probabilities ($p$), we estimated the average time spent within each 
-  of the states using 1000 simulations of a Bernoulli process where we continued to draw until transitioning
-  out of the state with probability $1 - p$. Of the prevalent states, states 1 and 
-  2 exhibit the shortest dwell times alongside their high covariances. States 5 and 7 have the longest dwell times in the pore and tail regions respectively.
+  parameters. Higher values of $\lambda_{\Sigma}$ generally are indicative of large fluctuations
+  and higher values of $\lambda_A$ indicate strong previous-hop dependence of the fluctuations.
+  (c) Using Equation~\ref{eqn:dwell_times}, we estimated the expected time spent within each 
+  of the states.
   }\label{fig:common_states_MET}
   \end{figure}
+
+  % BJC2: Again, this will change, but will follow the same general flow
+%  We can begin to dissect the dynamics of each state by studying their parameters.
+%  States 1, 3 and 5 have radial means near 1 nm or less (see y axis of $r$ direction 
+%  plot in Figure~\ref{fig:common_states_MET_lines}), which suggest that they occur
+%  close to the pore centers. States 2, 4, 6 and 7 occur well within the tail region
+%  of the membrane. States 1 and 2 have higher covariances in both the axial and radial
+%  directions compared to all other states. Covariance in each dimension appears to have
+%  a strong correlation. States 3 and 5 (in the pore region) as well as states 4, 6 and
+%  7 (in the tail region) are primarily distinguished based on their autoregressive 
+%  coefficients, A. Higher values of A generally lead to more wandering about the state
+%  mean. One could argue that the parameters of states 3--7 are actually very close which
+%  suggests that solutes might behave alike in morphologically distinct regions of the 
+%  membrane.
+%
+%  Despite some similarity in their VAR parameters, the length of time spent in states 
+%  3--7 appears to be dependent on the solute's radial location. Based on the 
+%  self-transition probabilities, we estimated the average time spent by each solute in
+%  each state (Figure~\ref{fig:dwell_times_MET}). States 3, 5 and 7 have long dwell times
+%  relative to the rest because they have high self-transition probabilities. Somewhat 
+%  surprisingly, both states 3 and 5 correspond to solutes located close to a pore center,
+%  where one might expect solute motion to be less restricted. Although solutes in states
+%  4 and 6 are in the viscous tail region, their dwell times are only intermediate. This
+%  could be due to inhomogeneity in the tail region which causes transitions between many
+%  different trapped states but with little net effect on solute MSD. However, there are
+%  instances of states within the tail region with dwell times that exceed 100--200 ns,
+%  as shown by our inclusion of state 7. There are no other states with dwell times longer
+%  than state 5 in the pore region.
+%  
+%  States 1 and 2 exhibit the shortest dwell times of the states studied. This is 
+%  consistent with the trajectory in Figure~\ref{fig:mechanism_map}. State 2 is the 
+%  shortest lived state, appearing to bridge other tail region states. State 1 
+%  appears to represent a significant hopping state. It has a high covariance and
+%  occurs near the pore center, where there is less obstruction to solute motion.
+%  It's dwell time of ca.~8 ns, suggests that solutes stay in this highly mobile 
+%  state for long enough for their positions to displace significantly.
 

### 2020-05-14 Ben_Manuscripts/hdphmm/Supporting_Information.tex
New supporting figures and mods to draft

@@
 
-  \subsection{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
+  \section{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
 
@@
 
+  \section{Deviations of the IHMM from Molecular Motion}\label{section:shorttimes_msd}
+
+   At extremely short time lags, the MSD is generally over-predicted by the IHMM
+  (see Figure~\ref{fig:unclustered_msd_shortlag}) because the VAR(1) model assumes
+  multivariate Gaussian noise while the MD data suggests the noise is better 
+  modeled by more general L\'evy stable noise. The first time lag of the MSD is
+  equivalent to the variance of all observed fluctuations (first-order difference). 
+  The IHMM simulation appears to over-estimate the variance because the actual 
+  distribution of solute fluctuations has heavy tails with a smaller variance (Figure~\ref{fig:emission_widths}).
+  The total distribution of hops is expected to be heavy tailed because it is a
+  combination of hop distributions from many states with different variances. More
+  interestingly, in Figure ~\ref{fig:state_emission_widths}, we show that the 
+  emission distribution of a single state picked out by the IHMM is fit better by
+  a more general L\'evy distribution while the emissions from IHMM realizations are
+  Gaussian, as expected. An improvement to the IHMM that may allow dynamics more 
+  faithful to MD would use an autoregressive model with L\'evy stable noise. However,
+  this would be less computationally efficient due to lack of conjugate priors.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{unclustered_msd_MET_shortlag.pdf}
+  \caption{}\label{fig:unclustered_msd_shortlag}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{emission_widths.pdf}
+  \caption{}\label{fig:emission_widths}
+  \end{subfigure}
+  \begin{subfigure}{0.32\textwidth}
+  \includegraphics[width=\textwidth]{state_emission_widths.pdf}
+  \caption{}\label{fig:state_emission_widths}
+  \end{subfigure}
+  \caption{(a) At short time lags, the MD MSD (black) and the IHMM MSD (orange)
+  differ significantly in their shape and curvature. (b) While the 
+  fluctuations in $z$ of both distributions are heavy-tailed, fitting well to zero-centered
+  symmetric L\'evy stable distributions with stability parameters, $\alpha$, the IHMM has
+  a wider variance. (c) The distribution of fluctuations in a chosen state frequently
+  visited by methanol is heavy tailed, but the IHMM is constrained to produce fluctuations
+  from a multivariate normal distribution ($\alpha$=2 in each dimension).
+  }\label{fig:short_timelags}
+  \end{figure}
+
+  Also apparent from Figure~\ref{fig:unclustered_msd_shortlag} is that the 
+  curvature of the MD MSD is far more gradual than that generated by the IHMM.
+  This is because the VAR(1) model is only correlated to its previous fluctuation
+  while the MD simulations suggest that correlation persists for at least tens
+  of nanoseconds.
+    % BJC2: could probably use a correlation function to suggest the AR order and stick the plot in SI
+  One may be able to reproduce the curvature at short time lags with higher order
+  VAR models, but it becomes a much higher dimensional parameterization that would
+  require significantly more data in order to produce stable results. Since we 
+  are interested in reproducing longer time scale behavior, it is not an issue of
+  great concern.
+
+  \section{Influence of number of clusters on qualitative hybrid trajectories}
+
+  \begin{figure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{qualitative_clustered_MET_20.pdf}
+  \caption{20 clusters}\label{fig:qualitative_20}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{qualitative_clustered_MET_30.pdf}
+  \caption{30 clusters}\label{fig:qualitative_30}
+  \end{subfigure}
+  \caption{The quality of hybrid trajectories resulting from clustered parameters
+  sets qualitatively improves as the number of clusters is increased. This comes 
+  at the cost of a larger state space to interpret.}\label{fig:qualitative_improvement}
+  \end{figure}
+
 \end{document}

### 2020-05-14 Ben_Manuscripts/hdphmm/Draft.tex
Saving significant progress on the mechanistic front

@@
 
-  \textit{Relating Parameters to Solute-Membrane Interactions}: Most of what we 
-  have learned thus far has been based on the parameters of our model with some 
-  qualitative validation using a single methanol trajectory. While 
-  we may be able to further corroborate our arguments by analyzing more
-  individual trajectories, it is more useful to correlate the state behavior with
-  solute-membrane interactions.
-
-  %BJC2: A lot of the following will probably be reworked with different clustering scheme
-%  \textit{Hydrogen Bonding Patterns}: 
-  The types of hydrogen bonding undergone by solutes is dependent on radial
-  location (see Figure~\ref{fig:hbond_pichart}). States with radial means near 1 nm
-  or less (states 1, 3 and 5) typically hydrogen bond with the monomer carboxylate
-  groups and ether linkages. States with radial means greater than 1 nm (states 2,
-  4, 6 and 7) tend to hydrogen bond with the monomer tails. Our previous work has
-  shown that there is a gradual transition from the hydrophilic to hydrophobic region in
-  these membranes, meaning the monomer location is not tightly bound in $r$. 
-  %MRS: above logic is not clear?
-  Therefore, there are instances of hydrogen bond interactions that one might consider 
-  uncharacteristic based on the state's radial mean.
-  %MRS: what is implication of ``uncharacteristicness''?
-
-  States which exhibit longer dwell times have longer hydrogen bond lifetimes (see
-  Figure~\ref{fig:hbond_pichart}). States 3--7 have significantly longer hydrogen 
-  bond lifetimes than states 1 and 2. It makes physical and mathematical sense that
-  states 1 and 2 should not stay trapped by hydrogen bonding for long periods because
-  they typically take large hops as communicated by their large covariances.
-  In the tail states, hydrogen bond lifetimes appear to increase with their dwell 
-  times. However, in the pores, the same linear relationship does not hold.
-  For example, state 5 has the lowest hydrogen bond lifetime of states 3--7
-  despite having the second longest dwell times.
-
-  The local density experienced by solutes may have an impact on the length of solute 
-  entrapment. On average, solutes in state 5 are surrounded by a relatively high density
-  of particles. Based on its radial location and preference towards hydrogen bonding
-  with the ether linkages (see Figure~\ref{fig:hbond_pi_charts}), it is reasonable to
-  assume that while in state 5, methanol spends most of its time just outside the 
-  pore region, sandwiched between the monomer head groups. Although state 5 hydrogen
-  bonds break more frequently than one might expect for a state with long dwell times,
-  it is possible that the solute's dense surroundings prevent it from wandering off 
-  before the hydrogen bonding interaction can be recovered. This may explain the 
-  behavior of the methanol in state 5 of the trajectory in Figure~\ref{fig:mechanism_map}
-  where the solute's center of mass appears to move more freely about its mean than 
-  other trapped states. The data suggests that methanol molecules in state 3 lie closer
-  to the pore center than state 5 because they tend to hydrogen bond most frequently 
-  with the carboxylate groups. Methanol molecules which experience state 3 are subject 
-  to a lower density local environment and rely more heavily on hydrogen bonding interactions, 
-  evidenced by their longer lifetimes, to stay trapped.
-
-  States describing behavior in the tail region show a direct relationship between 
-  hydrogen bond lifetimes and local density. Methanol molecules which experience state 2 
-  spend their time in a low density region of the tails where they can easily break free
-  of hydrogen bonds. Conversely, methanol molecules trapped in state 7 are in the densest 
-  region of all states studied. It is likely difficult for methanol to escape these high 
-  density regions and its position is further stabilized via hydrogen bonding.
-
-  %BJC4: I didn't put sodium ion association in this figure because it's infrequent. 
-  %BJC4: If I compare to acetic acid or urea, I could add it back. I was thinking of splitting
-  % the pi chart in half with slices corresponding to hbonds on one side and association on the other
+  \textit{Relating Parameters to Solute-Membrane Interactions}: Based on the
+  molecules and ions in the system, it is straightforward to hypothesize two types
+  interactions that might occur.
+  \begin{itemize}  
+    \item All of the solutes are polar and have hydrogen bond donating and 
+    accepting groups. 
+    \item The monomers have 10 oxygen atoms distributed from head to tail that are 
+    capable of accepting hydrogen bonds. 
+    \item Also, the ionic bond between the head groups and sodium ions can
+    be easily broken since both components can be stabilized by surrounding 
+    water molecules and solutes.
+    \item Therefore, it is logical to search for hydrogen bonding interactions
+    and solute assocation with sodium ions.
+  \end{itemize}
+
+  For methanol, hydrogen bonding is a much more dominant interaction than sodium
+  ion association. 
+  \begin{itemize}
+    \item In Figure~\ref{fig:hbond_fractions}, we show that methanol participates
+    in hydrogen bonds to various parts of the monomer between 27 and 45 \% of the
+    total time it occupies the dominant states.
+    \item Methanol associates with sodium ions less than 10 \% of the time in 
+    dominant states.
+  \end{itemize}
+
+  The distribution of types of hydrogen bonds and associated hydrogen bond lifetimes
+  varies by dominant state.
+  \begin{itemize}
+    \item States 1 and 2 are dominated by hydrogen bonds to the head groups and, to 
+    a smaller extent, the ether linkages.
+    \item State 1 methanol molecules that donate hydrogen bonds to the tail oxygen 
+    atoms exhibit by far the longest hydrogen bond lifetimes among all states.
+    \item States 3 and 4 hydrogen bond to all regions of the monomer relatively 
+    evenly, which is consistent with our earlier observation that states 3 and 4
+    are representative of behavior seen radially throughout the membrane pores.
+    \item State 3 has the lowest hydrogen bond and sodium association lifetimes 
+    which is consistent with its short dwell times. These are fleeting interactions
+    since it is likely a jumping state.
+    \item Methanol molecules in state 5 hydrogen bond almost exclusively to the 
+    carboxylate head groups and ether linkages which is consistent with the radial
+    ean of the cluster.
+  \end{itemize}
+
   \begin{figure}
   \centering
-  \begin{subfigure}{0.54\textwidth}
-  \includegraphics[width=\textwidth]{hbond_pi_charts.pdf}
-  \caption{}\label{fig:hbond_pi_charts}
-  \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{hbond_lifetimes_density_MET.pdf}
-  \caption{}\label{fig:hbond_lifetimes_density_MET}
-  \end{subfigure}
-  %MRS: legend doesn't show stripes.
-  \caption{(a) Methanol hydrogen bonds in different segments of the LLC monomer
-  dependent on the state. States with mean radial locations in the pore region tend to
-  hydrogen bond with the head groups and ether linkages. States with mean radial
-  locations in the tails tend to hydrogen bond with the tail oxygen atoms.
-  (b) Hydrogen bond lifetimes and the local density experienced by methanol
-  molecules can help us to understand dynamical states in terms of membrane 
-  interactions. The bars are colored according to match the states in Figures~\ref{fig:mechanism_map}
-  and~\ref{fig:common_states_MET}. States 1 and 2, which have large covariances, also have short
-  hydrogen bond lifetimes and exist in relatively low density regions. The
-  hydrogen bond lifetimes of methanol in states with radial means in the tail
-  region tend to increase with local density and mean dwell times. 
-  %MRS7: not clear from graphic which ones are in the pore.
-  %MRS7: is there any legend for the color for b? If same as above figure, indicate. Don't REALLY need color since they bars are already labeled, so it's 2 sources of duplicate information.
-  %BJC7: The state numbers are all you need to compare to the previous figure BUT the color make it easier 
-  %plot of the methanol trajectory where states aren't labeled.
-  %MRS7: cross-hatching doesn't appear in the legend? Not sure which is which (I assume hatched is number density because closer to that axis).
-  %BJC7: Is it because the hatches aren't dense enough? I see them in the legend
-  This monotonic
-  relationship does not exist for states in the pore region. The high 
-  local density experienced by state 5 methanol molecules may explain why 
-  hydrogen bond lifetimes are short but dwell times are high. State 5 methanol's
-  preference towards hydrogen bonds with ether linkages suggests that the solute
-  sits between LLC monomer head group which prevent it from wandering to far
-  before recovering its previous hydrogen bond.
-  }\label{fig:hbond_pichart}
+  \begin{subfigure}{0.475\textwidth}
+  \centering
+  \includegraphics[width=0.6\textwidth, angle=0]{monomer_oxygens.png}
+  \caption{}\label{fig:monomer_oxygens}
+  \end{subfigure}
+  \begin{subfigure}{0.475\textwidth}
+  \includegraphics[width=\textwidth]{hbond_fractions.pdf}
+  \caption{}\label{fig:hbond_fractions}
+  \end{subfigure}
+  \begin{subfigure}{0.475\textwidth}
+  \includegraphics[width=\textwidth]{hbond_lifetimes.pdf}
+  \caption{}\label{fig:hbond_lifetimes}
+  \end{subfigure}
+  % BJC4: I put this one here for compact-ness. Not sure if I should separate into own figure
+  \begin{subfigure}{0.475\textwidth}
+  \includegraphics[width=\textwidth]{association_fraction_lifetimes.pdf}
+  \caption{}\label{fig:association_fraction_lifetimes}
+  \end{subfigure}
+  \caption{(a) We analyzed hydrogen bond donation to the highlighted oxygen atoms in three 
+  regions of the monomer: the carboxylate groups (blue), the ether linkages (green) and the
+  tails (red). (b) For each dominant state, we plotted the fraction of the total time in
+  that state spent hydrogen bonding to various regions of the monomer, color coded to match (a).
+  (c) For each type of hydrogen bond in each dominant state, we calculated the 95th percentile
+  of hydrogen bond lifetimes. (d) We also analyzed the frequency and lifetimes of solute 
+  association with sodium ions. Methanol associates with sodium less than 10 \% of the total 
+  time it occupies any of the dominant state.
+  %Relative to hydrogen bonding, it is a relatively infrequenct interaction
+  %for methanol molecules, but the 
+  }
+  \label{fig:hydrogen_bonding}
   \end{figure}
+
+  The local number density of heavy atoms surrounding solutes help round out methanol's
+  mechanistic picture.
+  \begin{itemize}
+    \item Although hydrogen bonding interactions are relatively frequent, methanol molecules
+    are unbound by any measurable electrostatic interactions about half or more of the 
+    simulation time.  
+    \item Figure~\ref{fig:local_densities} helps to illustrate how the local density of 
+    membrane components can aid in solute entrapment.
+    \item When solutes experience long trapping times, the local number density of heavy 
+    atoms is larger.
+    \item Even when hydrogen bonds break, surrounding alkane density likely helps keep
+    the solutes in place allowing them to eventually reform. This can happen deep in the
+    tails or close to the monomer head groups.
+    \item Methanol molecules which experience State 3 have by far the smallest local 
+    number density which is likely responsible for their mobility, as suggested by the state's
+    large covariance.
+  \end{itemize}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{local_densities.pdf}
+  \caption{We measured the local number density of heavy atoms surrounding solutes in each
+  state. In blue, we plot the local number density experienced by solutes averaged over all
+  frames in which the solute occupied the given state. We broke down this overall average 
+  number density into number densities measured from instances when the state is occupied 
+  for long (orange) versus short(red) dwell time states. We define define `long' dwells times
+  as the 50th percentile of all dwell times in the given state, and short as all others. It
+  is clear that solutes which experience longer dwells times are also surrounded by more 
+  heavy atoms on average.}\label{fig:local_densities}
+  \end{figure}
+
+%BJC4: the following has pretty all been replaced.
+%  Most of what we 
+%  have learned thus far has been based on the parameters of our model with some 
+%  qualitative validation using a single methanol trajectory. While 
+%  we may be able to further corroborate our arguments by analyzing more
+%  individual trajectories, it is more useful to correlate the state behavior with
+%  solute-membrane interactions.
+%
+%  %BJC2: A lot of the following will probably be reworked with different clustering scheme
+%%  \textit{Hydrogen Bonding Patterns}: 
+%  The types of hydrogen bonding undergone by solutes is dependent on radial
+%  location (see Figure~\ref{fig:hbond_pichart}). States with radial means near 1 nm
+%  or less (states 1, 3 and 5) typically hydrogen bond with the monomer carboxylate
+%  groups and ether linkages. States with radial means greater than 1 nm (states 2,
+%  4, 6 and 7) tend to hydrogen bond with the monomer tails. Our previous work has
+%  shown that there is a gradual transition from the hydrophilic to hydrophobic region in
+%  these membranes, meaning the monomer location is not tightly bound in $r$. 
+%  %MRS: above logic is not clear?
+%  Therefore, there are instances of hydrogen bond interactions that one might consider 
+%  uncharacteristic based on the state's radial mean.
+%  %MRS: what is implication of ``uncharacteristicness''? 
+%
+%  States which exhibit longer dwell times have longer hydrogen bond lifetimes (see
+%  Figure~\ref{fig:hbond_pichart}). States 3--7 have significantly longer hydrogen 
+%  bond lifetimes than states 1 and 2. It makes physical and mathematical sense that
+%  states 1 and 2 should not stay trapped by hydrogen bonding for long periods because
+%  they typically take large hops as communicated by their large covariances.
+%  In the tail states, hydrogen bond lifetimes appear to increase with their dwell 
+%  times. However, in the pores, the same linear relationship does not hold.
+%  For example, state 5 has the lowest hydrogen bond lifetime of states 3--7
+%  despite having the second longest dwell times.
+
+%  The local density experienced by solutes may have an impact on the length of solute 
+%  entrapment. On average, solutes in state 5 are surrounded by a relatively high density
+%  of particles. Based on its radial location and preference towards hydrogen bonding
+%  with the ether linkages (see Figure~\ref{fig:hbond_pi_charts}), it is reasonable to
+%  assume that while in state 5, methanol spends most of its time just outside the 
+%  pore region, sandwiched between the monomer head groups. Although state 5 hydrogen
+%  bonds break more frequently than one might expect for a state with long dwell times,
+%  it is possible that the solute's dense surroundings prevent it from wandering off 
+%  before the hydrogen bonding interaction can be recovered. This may explain the 
+%  behavior of the methanol in state 5 of the trajectory in Figure~\ref{fig:mechanism_map}
+%  where the solute's center of mass appears to move more freely about its mean than 
+%  other trapped states. The data suggests that methanol molecules in state 3 lie closer
+%  to the pore center than state 5 because they tend to hydrogen bond most frequently 
+%  with the carboxylate groups. Methanol molecules which experience state 3 are subject 
+%  to a lower density local environment and rely more heavily on hydrogen bonding interactions, 
+%  evidenced by their longer lifetimes, to stay trapped.
+%  
+%  States describing behavior in the tail region show a direct relationship between 
+%  hydrogen bond lifetimes and local density. Methanol molecules which experience state 2 
+%  spend their time in a low density region of the tails where they can easily break free
+%  of hydrogen bonds. Conversely, methanol molecules trapped in state 7 are in the densest 
+%  region of all states studied. It is likely difficult for methanol to escape these high 
+%  density regions and its position is further stabilized via hydrogen bonding.
+%  
+%  %BJC: I didn't put sodium ion association in this figure because it's infrequent. 
+%  %BJC: If I compare to acetic acid or urea, I could add it back. I was thinking of splitting
+%  % the pi chart in half with slices corresponding to hbonds on one side and association on the other
+%  \begin{figure}
+%  \centering
+%  \begin{subfigure}{0.54\textwidth}
+%  \includegraphics[width=\textwidth]{hbond_pi_charts.pdf}
+%  \caption{}\label{fig:hbond_pi_charts}
+%  \end{subfigure}
+%  \begin{subfigure}{0.45\textwidth}
+%  \includegraphics[width=\textwidth]{hbond_lifetimes_density_MET.pdf}
+%  \caption{}\label{fig:hbond_lifetimes_density_MET}
+%  \end{subfigure}
+%  %MRS: legend doesn't show stripes.
+%  \caption{(a) Methanol hydrogen bonds in different segments of the LLC monomer
+%  dependent on the state. States with mean radial locations in the pore region tend to
+%  hydrogen bond with the head groups and ether linkages. States with mean radial
+%  locations in the tails tend to hydrogen bond with the tail oxygen atoms.
+%  (b) Hydrogen bond lifetimes and the local density experienced by methanol
+%  molecules can help us to understand dynamical states in terms of membrane 
+%  interactions. The bars are colored according to match the states in Figures~\ref{fig:mechanism_map}
+%  and~\ref{fig:common_states_MET}. States 1 and 2, which have large covariances, also have short
+%  hydrogen bond lifetimes and exist in relatively low density regions. The
+%  hydrogen bond lifetimes of methanol in states with radial means in the tail
+%  region tend to increase with local density and mean dwell times. 
+%  %MRS7: not clear from graphic which ones are in the pore.
+%  %MRS7: is there any legend for the color for b? If same as above figure, indicate. Don't REALLY need color since they bars are already labeled, so it's 2 sources of duplicate information.
+%  %BJC7: The state numbers are all you need to compare to the previous figure BUT the color make it easier 
+%  %plot of the methanol trajectory where states aren't labeled.
+%  %MRS7: cross-hatching doesn't appear in the legend? Not sure which is which (I assume hatched is number density because closer to that axis).
+%  %BJC7: Is it because the hatches aren't dense enough? I see them in the legend
+%  This monotonic
+%  relationship does not exist for states in the pore region. The high 
+%  local density experienced by state 5 methanol molecules may explain why 
+%  hydrogen bond lifetimes are short but dwell times are high. State 5 methanol's
+%  preference towards hydrogen bonds with ether linkages suggests that the solute
+%  sits between LLC monomer head group which prevent it from wandering to far
+%  before recovering its previous hydrogen bond.
+%  }\label{fig:hbond_pichart}
+%  \end{figure}
 

### 2020-05-14 Ben_Manuscripts/hdphmm/Draft.tex
New Figures and finished outline of mechanistic section

@@
   We applied the IHMM independently to all 24 trajectories of each of the four solutes studied.
-  The number of states found for each trajectory varied between 5 and 30.  %BJC2: MET: (5, 28)
+  The number of states found for each trajectory varied between 5 and 30.  %BJC4: MET: (5, 28), need to finalized
   In Figure~\ref{fig:rz_unclustered}, we show the state sequence determined by the IHMM for
@@
 
-  In Figure~\ref{fig:unclustered_msds}, we show that we can reproduce the 
+  In Figure~\ref{fig:unclustered_msds}, we show that in most cases we can reproduce the 
   MD MSDs on long timescales within uncertainty using realizations of the 
@@
     in their long term predictions.
+    \item We underestimate the MSD of Urea because of a small number of MD 
+    trajectories with uncharacteristically high MSDs. Despite our best efforts, 
+    we could not adequately parameterize an IHMM which reproduced said 
+    behavior. (see SI)  %BJC4: TODO
+    \item On long timescales, the model appear to have the same slope as 
+    the MD trajectory.
   \end{itemize}
@@
 
-  %BJC4: figure here
-
-  %BJC4: some kind of brief selectivity analysis here
+  % BJC4: figure here
+
+  % BJC4: some kind of brief selectivity analysis here. This easy, I'll get that done 
+  % tonight or tomorrow.
 
@@
   \caption{(a) Stochastic trajectory realizations generated from our model (blue) based on
-  the clustered methanol parameters do not qualit}\label{fig:clustered_dynamics}
+  the clustered methanol parameters do not qualitatively reproduce the diversity of behavior
+  seen in our MD trajectories. (b) MSD predictions by clustered parameter sets consistently
+  under-predict MD MSD. They appear to do a better job of predicting MSDs as the number
+  of clusters increases.}\label{fig:clustered_dynamics}
   \end{figure}
-
-%  \begin{figure}
-%  \centering
-%  % BJC4: combine (a) and (b). Add figure with MSD prediction
-%  \begin{subfigure}{0.32\textwidth}
-%  \includegraphics[width=\textwidth]{dwell_distributions.pdf}
-%  \caption{}\label{fig:dwell_distributions}
-%  \end{subfigure}
-%  \begin{subfigure}{0.32\textwidth}
-%  \includegraphics[width=\textwidth]{dwell_distributions_modT.pdf}
-%  \caption{}\label{fig:dwell_distributions_modT}
-%  \end{subfigure}
-%  \begin{subfigure}{0.32\textwidth}
-%  \includegraphics[width=\textwidth]{unclustered_msd_MET_modT.pdf}
-%  \caption{}\label{fig:msd_modT}
-%  \end{subfigure}
-%  \caption{(a) The density of short dwell times compiled from realizations of
-%  the IHMM fit to methanol trajectories is below that measured directly from 
-%  the MD trajectories. If we modify the transition matrix in order to favor 
-%  transitions towards states with short dwell times, we can more closely match
-%  the (b) dwell time distributions and (c) MSDs.}\label{fig:slow_T}
-%  \end{figure}
-
-% BJC: probably a bad idea
-%  It may still be possible to use these hybrid trajectories in order to predict
-%  selectivity since they undershoot the MD MSD by a consistent number and 
-%  the ratios will stay the same.
-
-  % BJC2: the numbers and choices of states in this paragraph will change, but I think we
-  % can still use this framework to study mechanisms.
-
-%  \subsubsection*{Relating Clusters to Mechanisms}
-%  
-%  The parameters of each cluster can be related to dominant solute-membrane interactions.
-%  \begin{itemize}
-%    \item Based on our previous work, we know that hydrogen bonding, sodium ion 
-%    association and radial location within the membrane pores will have a significant
-%    influence on transport properties. 
-%    \item Even without our previous work, it would still be easy to speculate that these 
-%    interactions might occur and could therefore be used to help understand the 
-%    states identified by the IHMM.
-%    \item We have also incorporated membrane density as a physical metric because we 
-%    know the membrane has an inhomogeneous structure.
-%  \end{itemize}
-
-%  \textit{Learning from individual trajectories}: In Figure~\ref{fig:mechanism_map}, 
-%  we demonstrate the wide range of behavior exhibited by a representative 2D methanol
-%  trajectory.
-%%BJC2: reducing duplication
-%%  The coordinates
-%%  are colored according to the cluster with which methanol's dynamics are most consistent,
-%%  which implies that this particular methanol trajectory exhibits eight distinct dynamical 
-%%  behaviors (in order of their first appearance, they are colored dark yellow, red, light
-%%  blue, light green, orange, blue, teal and lime green).
-%  The solute time series are coupled with color coded bars which describe the solute's
-%  local environment and physical interactions that it undergoes at each trajectory frame. 
-%%  From the top, they describe 
-%%  whether the solute is associated with sodium, whether the solute is hydrogen bonding
-%%  with the monomer as well as to what part of the monomer it is hydrogen bonding, and 
-%%  finally, the local number density surrounding the solute. 
-%
-%  %BJC2: the exact figure will change, but most of what I say shouldn't
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.75\textwidth}
-%  \includegraphics[width=\textwidth]{mechanism_map.png}
-%  \caption{}
-%  \end{subfigure}
-%  \begin{subfigure}{0.24\textwidth}
-%  \includegraphics[width=\textwidth]{monomer_oxygens.png}
-%  \caption{}
-%  \end{subfigure}
-%  %MRS: a lot of this caption test is duplicated from the main text. I would suggest reducing the duplication.
-%  %BJC: you think better to have more detail in text or in caption?
-%  %MRS2: at a certain point, it should be in the text.  In the caption, I would just state what the point of the plot is, 
-%  % and define the colors/data/etc.  But full explanation would be better in the text. Captions should be scannable quickly,
-%  % based on how people process papers, and this should be significantly shorter for readability. 
-% \caption{(a) We can learn a significant amount of detail about solute motion by viewing 
-%  solute trajectories color-coded according to their clustered dynamical behavior alongside
-%  plots of the dominant molecular interactions and descriptions of the membrane's local 
-%  environment. In the plot above, we show the radial and axial coordinates of a single
-%  methanol molecule over the course of the equilibrated portion of its MD simulation.
-%  Disjoint segments of the same color imply the solute behaves similarly at different 
-%  points of the trajectory because their VAR parameters place them in the same cluster. 
-%  There are eight distinct dynamical modes exhibited by this trajectory. In order
-%  of their first appearance, they are colored dark yellow, red, light blue, light green,
-%  orange, blue, teal and lime green. On the top of the plot are bars which represent different
-%  physical interactions and the membrane's local environment as a function of time. The top 
-%  bar is colored green at time points where solutes are associated with sodium. Methanol 
-%  associates with sodium ions relatively infrequently. The next bar down is colored when hydrogen
-%  bonds exist. The colors match the enlarged oxygen atoms highlighted in (b). Blue slivers
-%  correspond to hydrogen bonds donated to the monomer's carboxylate head group. Green slivers
-%  correspond to  hydrogen bonds donated to the ether linkages between the head groups
-%  and tails. Red slivers correspond to hydrogen bonds donated to the oxygens on the ends
-%  of the monomer tails. Methanol exhibits significant hydrogen bonding with all parts of
-%  the monomer. Which part of the monomer methanol hydrogen bonds to is heavily correlated
-%  to the solute's $r$ coordinate. Finally, the bar with the blue gradient represents the local 
-%  membrane density based on the solute's ($r$, $z$) coordinate. Darker shades of blue
-%  correspond to higher membrane densities. The density appears to be higher when methanol
-%  motion is restricted (e.g. from 75 to 550 ns). It is relatively low in areas where methanol's
-%  position fluctuates significantly (e.g. from 550 to 700 ns). 
-%  }\label{fig:mechanism_map}
-%  \end{figure}
-%
-%  One can gain useful chemical intuition just by studying plots like 
-%  Figure~\ref{fig:mechanism_map}. It is clear that, for methanol, association 
-%  with sodium is a much rarer interaction than hydrogen bonding with the 
-%  LLC monomers. Methanol hydrogen bonds to all regions of the monomers dependent
-%  on its radial position. Its fluctuations tend to be smallest when hydrogen bonded
-%  or in areas of high local number density. For example, from approximately 75 to 
-%  525 ns, methanol appears to be trapped in a high density region of the tails.
-%  In the time that follows, it enters a region of relatively low density where 
-%  fluctuations are quite large. During this time period, there is intermittent, 
-%  short-lived hydrogen bonding with the oxygen atoms at the tail ends, as suggested
-%  by the frequent state changes during that time period and red slivers in the bar
-%  above. Significant hops in the $z$ direction appear to be described by the dark blue
-%  state. After entering the dark blue state ca. 850 ns, methanol appears to jump
-%  significantly in the $z$ direction from a hydrogen bonded state with the ether 
-%  linkages to a hydrogen bonded state with a head group in a monomer below it.
 
@@
   	solute trajectories (Figure~\ref{fig:prevalence}).
-  	\item Although a majority of the solutes visit these 5 states the
+  	\item Although a majority of the solutes visit these 5 dominant states the
   	amount of time spent in each varies widely. 
@@
   	eigenvalue of the covariance matrix.
-  	\item Both eigenvalues are actually of state 3's covariance are actually quite
+  	\item Both eigenvalues of state 3's covariance are actually quite
   	large. This implies relatively large fluctuations in the $z$ direction and even
@@
     the shortest dwell times while the rest have intermediate dwell times.
-    \item This is partially confirmed via inspection of Figure~\ref{fig:clustered_traj_MET},
+    \item This is somewhat supported by inspection of Figure~\ref{fig:clustered_traj_MET},
     however. 
-    \item Once again, since we clustered, it is important to avoid distraction
-    by the exact dwell time values, and to focus on their relative magnitudes
-  \end{itemize}
-
-  % BJC4: Not sure if this is useful. Maybe can replace above three paragraphs 
-  % with this. Helps us look for mechanisms.
+	\item The expected dwell times of the clusters incorporate all 24 trajectories.
+%    \item Once again, since we clustered, it is important to avoid studying
+%    the exact dwell time values, and to focus on their relative magnitudes.
+  \end{itemize}
+
+  % BJC4: Not sure if this is useful.
   By studying the parameters, it is now easier to describe the state behavior.
@@
 
-  % BJC2: Again, this will change, but will follow the same general flow
-%  We can begin to dissect the dynamics of each state by studying their parameters.
-%  States 1, 3 and 5 have radial means near 1 nm or less (see y axis of $r$ direction 
-%  plot in Figure~\ref{fig:common_states_MET_lines}), which suggest that they occur
-%  close to the pore centers. States 2, 4, 6 and 7 occur well within the tail region
-%  of the membrane. States 1 and 2 have higher covariances in both the axial and radial
-%  directions compared to all other states. Covariance in each dimension appears to have
-%  a strong correlation. States 3 and 5 (in the pore region) as well as states 4, 6 and
-%  7 (in the tail region) are primarily distinguished based on their autoregressive 
-%  coefficients, A. Higher values of A generally lead to more wandering about the state
-%  mean. One could argue that the parameters of states 3--7 are actually very close which
-%  suggests that solutes might behave alike in morphologically distinct regions of the 
-%  membrane.
-%
-%  Despite some similarity in their VAR parameters, the length of time spent in states 
-%  3--7 appears to be dependent on the solute's radial location. Based on the 
-%  self-transition probabilities, we estimated the average time spent by each solute in
-%  each state (Figure~\ref{fig:dwell_times_MET}). States 3, 5 and 7 have long dwell times
-%  relative to the rest because they have high self-transition probabilities. Somewhat 
-%  surprisingly, both states 3 and 5 correspond to solutes located close to a pore center,
-%  where one might expect solute motion to be less restricted. Although solutes in states
-%  4 and 6 are in the viscous tail region, their dwell times are only intermediate. This
-%  could be due to inhomogeneity in the tail region which causes transitions between many
-%  different trapped states but with little net effect on solute MSD. However, there are
-%  instances of states within the tail region with dwell times that exceed 100--200 ns,
-%  as shown by our inclusion of state 7. There are no other states with dwell times longer
-%  than state 5 in the pore region.
-%  
-%  States 1 and 2 exhibit the shortest dwell times of the states studied. This is 
-%  consistent with the trajectory in Figure~\ref{fig:mechanism_map}. State 2 is the 
-%  shortest lived state, appearing to bridge other tail region states. State 1 
-%  appears to represent a significant hopping state. It has a high covariance and
-%  occurs near the pore center, where there is less obstruction to solute motion.
-%  It's dwell time of ca.~8 ns, suggests that solutes stay in this highly mobile 
-%  state for long enough for their positions to displace significantly.
-
   \textit{Relating Parameters to Solute-Membrane Interactions}: Based on the
-  molecules and ions in the system, it is straightforward to hypothesize two types
-  interactions that might occur.
+  molecules and ions which constitute the membrane, it is straightforward to 
+  hypothesize two types interactions that might occur.
   \begin{itemize}  
@@
     carboxylate head groups and ether linkages which is consistent with the radial
-    ean of the cluster.
+    mean of the cluster.
   \end{itemize}
@@
   \subsubsection*{Comparison of Solute Behavior}
-  %BJC2: Again, most of this section will get a facelift, but will try to follow same flow 
-  We applied similar analysis to the other three solutes in this study: urea, acetic acid
-  and ethylene glycol. Not only can we use the model to study the dynamics of each 
-  solute individually, but we can compare their behavior in order to improve our
-  understanding of more subtle mechanistic details.
+
+  We can apply a similar analysis to the other solutes in this study. We can likely
+  learn new information through comparison of solute behavior with metrics based on
+  the chemical intuition gained by studying methanol.
 
   The size and chemical functionality of the solutes dictates the interactions which
-  influence solute transport. In Figure~\ref{fig:hbonds_assoc_summary}, we show that
-  the solutes donate hydrogen bonds and associate with sodium ions to varying degrees.
-  We also show the solute MSDs after a 1000 ns time lag. It is not immediately obvious
-  why the MSDs follow this trend. 
-  %MRS2: be more precise what ``this trend'' is.
-  The states identified by the IHMM shed
-  some light on the reasoning.
+  influence solute transport.
+  \begin{itemize}
+    \item In Figure~\ref{fig:hbonds_assoc_summary}, we show that the solutes donate
+    hydrogen bonds and associate with sodium ions to varying degrees.
+    \item In fact methanol, by far, interacts the least by these mechanisms.
+    \item This is likely because methanol is very small and it is easier for it to partition
+    into the tail region where there are fewer groups with which it can interact (see
+    Figure~\ref{fig:rdf_summary}).
+    \item Acetic acid, urea and ethylene glycol are slightly larger than methanol
+    and contain multiple polar substituents which stabilize them closer to the 
+    pore region.
+    \item These three solutes also participate in significantly more sodium ion
+    association. 
+    \item In our previous work, we showed that the sodium ions frequently associate
+    with the carbonyl groups of acetic acid and urea.
+  \end{itemize}
 
@@
   \centering
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{hbonds_assoc_summary.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{rdf_summary.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
+  \begin{subfigure}{0.325\textwidth}
   \includegraphics[width=\textwidth]{dwell_time_summary.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.45\textwidth}
-  \includegraphics[width=\textwidth]{cov_summary.pdf}
-  \caption{}\label{fig:cov_summary}
-  \end{subfigure}
-  %MRS7: is c) methanol?  I thought it wasn't associating with Na+ much.
-  %BJC7: looks about 5 %, certainly less than the other. I could add
-  % some discussion of this to previous section.
-  %MRS: methanol yellow is hard to see in (b). Maybe add outlines to histogram?  I guess they are, increase alpha or something for yellow?
-  %MRS: check consistency of capitalization in legend in (c) 
   \caption{(a) Solutes hydrogen bond and associate with sodium ions
   to different degrees. Sometimes, they participate in both interactions at
-  once. The frequency at which solutes interact via either mechanism does
-  not appear to be linearly related to the solute's mean squared displacement
-  after a 1000 ns time lag. (b) We histogrammed the means of the clusters weighted
-  by the number of fluctuation within that cluster. Most solutes spend the majority of
-  their time close to the pore center. Only methanol has a significant peak
-  beyond 1.5 nm from the pore center. (c) The trend in the maximum dwell time
-  among prevalent states for each solute is inversely related to the
-  solute's MSD. In some cases, non-prevalent states show very long dwell times,
-  which may have a significant impact on solute MSD. (d) All solutes tend to
-  take larger hops in the $z$ direction when they are in the pore versus in 
-  the tails. All solutes except urea make slightly larger radial hops while 
-  in the tails.
-  %BJC6: I made this plot out of curiosity, not sure if I'll use it yet.
+  once. (b) We histogrammed the radial means of the unclustered states weighted
+  by the length of time spent in that state. Most solutes spend the majority of
+  their time close to the pore center. Only methanol has a significant density
+  far from the pore center. (c) The largest expected dwell time among the dominant 
+  clustered states for each solute are inversely related to the solute's MSD. 
   }\label{fig:summaries}
@@
 
-  Hydrogen bonding and sodium ion association interactions are far more 
-  common when solutes stay near the pore centers. In Figure~\ref{fig:rdf_summary},
-  we plot the distribution of the radial means of each cluster weighted by 
-  the time spent in that cluster. All solutes except methanol spend the 
-  majority of their time near the pore centers (roughly defined as within 
-  1.5 nm). As we showed earlier, methanol spends a significant portion of its
-  time trapped in the dense tails.
-
-  % BJC: we can probably use this to create a new definition of the pore and tail region.
-  % and perhaps focus on transitions between them.
-  Solute size likely has a large effect on their preferred radial location within
-  the pores. The histograms in Figure~\ref{fig:rdf_summary} have a clear vacancy 
-  between what one might consider the pore and tail region, most evident in methanol's 
-  distribution of radial positions. The area between the head groups and the distal
-  regions of the tails is dense and hydrophobic which creates a considerable energy 
-  barrier to be overcome in order to transition to that region.
-  %BJC: I wonder if there is a state which corresponds to the jump from pore to tail region. Might be hard to pick up.
-  Methanol is the smallest solute in this study and therefore appears to 
-  have the easiest time crossing into the tails.
-
-  Despite their close proximity to the low density aqueous pore region, acetic
-  acid, ethylene glycol and urea exhibit a range of trapping behavior.
-  It is clear that the number of polar interactions is not directly
-  related to solute MSD. Acetic acid participates in a similar number of 
-  interactions relative to urea and ethylene glycol, but its MSD is considerably
-  lower. For the purpose of this analysis, as in the previous section, we 
-  defined states that appear in more than one third of the trajectories to
-  be prevalent states. In Figure~\ref{fig:dwell_time_summary}, we plot the\
-  longest dwell times exhibited by each solute among the prevalent states as 
-  well as out of all the states. The state which exhibits the longest dwell
-  times among all acetic acid states appears in 9 different trajectories, 
-  making it a prevalent state, and occurs 0.9 nm from the pore center.
-  Although urea possesses the state with the longest dwell time among the
-  solutes studied, it occurs in the tail region with prevalent states having 
-  much shorter dwell times. Ethylene glycol appears to be the least subject to
-  trapping.
-
-%  The combination of a carbonyl group, which binds strongly to sodium, and a 
-%  hydroxyl group, which can form strong hydrogen bonds, makes acetic acid
-%  particularly prone to trapping.
-%  BJC6: more complicated than this. I will revisit.
+  Solutes with dominant clusters characterized by long dwell times tend to 
+  have lower MSDs.
+  \begin{itemize}
+    \item In Figure~\ref{fig:dwell_time_summary}, we plot the expected dwell
+    time of each solute in the dominant state which has the the highest
+    self-transition probability. 
+    \item The trend in MSDs is inversely related to the trend in maximum
+    expected dwell times.
+    \item Both acetic acid and urea participate in many hydrogen bonds and
+    sodium ion association interactions and the states visited by both solutes
+    have similar distributions of radial means, however acetic acid is 
+    subject to much longer dwell times, and hence a lower MSD.
+    % BJC4: I could dig further into this. Not sure if worth it.
+    \item This may be because acetic acid is a stronger hydrogen bond donor
+    than urea. 
+    \item Could also be that the urea is still mobile while paired with sodium ions.
+  \end{itemize}
 
@@
   time series with an unknown number of latent dynamical modes. Initially, we applied
-  the algorithm to each trajectory independently. For each solute studied, this resulted
-  in over 300 distinct states. By clustering the parameter sets we were able to reduce 
-  the state space to 10\% of its original size by grouping states with similar VAR
-  parameters.
-
-  We coupled analysis of the clustered parameter sets with measurements of membrane 
-  properties and solute-membrane interactions in order to gain a detailed understanding
-  of the diverse sets behavior exhibited by solutes in these membranes. We showed how
-  solute motion is influenced by hydrogen bonding, sodium ion association and local
-  membrane density. These interactions have a direct impact on the size and
-  correlation of sequential solute steps.
-
-  Finally, we show how one can generate stochastic realizations of our model that
+  the algorithm to each trajectory independently. Using the model parameters fit
+  to each trajectory, we generated stochastic realizations of solute trajectories that
   can qualitatively and quantitatively reproduce the behavior of MD solute 
   trajectories. The realizations show the hopping and trapping behavior that is
-  characteristic of polar solutes in this system. We can also use them to reproduce
-  the solute MSDs measured from the MD trajectories. The low computational expense 
-  of generating these stochastic trajectories allows one to project solute behavior
-  on much longer timescales and thus predict experimentally-relevant macroscopic 
-  transport properties like solute flux and selectivity.
-
-  We showcase this modeling approach by example, but it is important to
+  characteristic of polar solutes in this system.
+
+  By pooling MSDs predicted by models fit to each trajectory, we can reproduce
+  the solute MSDs measured directly from the our MD-simulated trajectories. 
+  The low computational expense of generating these stochastic trajectories allows
+  one to project solute behavior on much longer timescales, allowing us to predict
+  selectivity, an experimentally-relevant quantity.
+
+  In order to gain a mechanistic understanding of solute motion, we showed how 
+  we could cluster the parameter sets in order to reduce the state space down
+  to an interpretable size. We coupled analysis of the clustered parameter sets
+  with measurements of membrane properties and solute-membrane interactions 
+  in order to gain a detailed understanding of the diverse sets behavior 
+  exhibited by solutes in these membranes. We showed how
+  solute motion is influenced by hydrogen bonding, sodium ion association and local
+  membrane density.
+
+  When clustering, our goal was to create the simplest model possible that gave
+  clear mechanistic insight. This is important for systems where transport mechanisms
+  are not easily hypothesized. However, once one gains some mechanistic understanding,
+  as we have in this work, the clustering procedure can be modified in order to 
+  study specific interactions or radially dependent behavior.
+
+  Although we showcase this modeling approach by example, but it is important to
   recognize the generality of this analysis, especially in the context of molecular

### 2020-05-15 Ben_Manuscripts/hdphmm/Draft.tex
Added a few comments
Updates to intro

@@
   systems which exhibit complex short timescale subdiffusive dynamics, one cannot 
-  calculate reliable diffusion constants since solute mean square displacements (MSDs)
-  are non-linear on the timescales accessible to molecular simulation. Therefore, we
-  are in need of a more flexible approach for modeling solute dynamics which makes 
-  less assumptions about the solute's average behavior.
-
-  In this work, we are particularly interested in the design of lyotropic liquid crystal (LLC)
-  monomers, a class of amphiphilic molecules whose ordered self-assembled phases can be 
-  cross-linked into mechanically strong membranes capable of highly selective separations.
-  \begin{itemize}
-  	\item Inverted hexagonal, H\textsubscript{II}, phase LLC membranes are characterized
-  	by hexagonally packed, uniform-sized and straight pores, an ideal geometry for high 
-  	throughput transport.
-	\item Their pores are lined with the LLC monomer functional groups which can
-	potentially be designed to interact with solutes in a chemically-specific manner.
-	\item It would be extremely useful to experimentalists if we could connect LLC monomer
-	design with measurable quantities.
-	\item This goal is complicated by the non-Brownian hopping and trapping behavior induced
-	by the membrane's diverse topology and inhomogeneous structure.~\cite{coscia_understanding_2019,coscia_chemically_2019}
-  \end{itemize}
+  calculate reliably compute diffusion constants since solute mean square 
+  displacements (MSDs) are non-linear on the timescales accessible to molecular simulation.
+  Therefore, we are in need of a more flexible approach for modeling solute dynamics
+  which makes less assumptions about the solute's short time scale behavior.
+
+  In this work, we are particularly interested in the design of lyotropic liquid 
+  crystal (LLC) monomers, a class of amphiphilic molecules whose ordered self-assembled
+  phases can be cross-linked into mechanically strong membranes capable of highly 
+  selective separations. Inverted hexagonal, H\textsubscript{II}, phase LLC membranes
+  are characterized	by hexagonally packed, uniform-sized and straight pores, an ideal
+  geometry for high throughput transport. Their pores are lined with the LLC monomer's
+  functional groups which can potentially be designed to interact with solutes in a 
+  chemically-specific manner. It would be extremely useful to experimentalists if we 
+  could connect LLC monomer design with measurable quantities. This goal is complicated
+  by the non-Brownian hopping and trapping behavior induced by the membrane's diverse
+  topology and inhomogeneous structure.~\cite{coscia_understanding_2019,coscia_chemically_2019}
 
@@
   from qualitative MD studies of solute transport in an H\textsubscript{II} phase LLC
-  membrane.~\cite{coscia_chemically_2019,coscia_capturing_2020}
-  \begin{itemize}
-    \item We identified three classes of trapping behavior which result in short time scale
-    subdiffusion.
-    \item In our first approach to stochastically model this behavior, we treated the
-    system's dynamics as a sequence of anti-correlated hops between power law distributed
-    periods of entrapment, a framework called subordinated fractional Brownian or L\'evy
-    motion.
-    \item In a second approach, we treated solute motion as a Markov state model with 
-    state-dependent dynamics, where we parameterized the state transition probabilities 
-    between each of eight discrete states, defined by the observed trapping mechanism, 
-    as well as the solute dynamics within each of these states. 
-    \item We showed how one could use realizations of any stochastic model like these in
-    order to predict macroscopic flux and selectivity. 
-  \end{itemize}
+  membrane.~\cite{coscia_chemically_2019,coscia_capturing_2020} We identified three 
+  classes of trapping behavior which result in short time scale subdiffusion. In our 
+  first approach to stochastically model this behavior, we treated the system's dynamics
+  as a sequence of anti-correlated hops between power law distributed periods of 
+  entrapment, a framework called subordinated fractional Brownian or L\'evy
+  motion.~\cite{thiel_weak_2014,teuerle_modeling_2013} In a second approach, we treated 
+  solute motion as a Markov state model~\cite{pande_everything_2010} with state-dependent
+  dynamics, where we parameterized the state transition probabilities between each of
+  eight discrete states, defined by the observed trapping mechanisms, as well as the 
+  solute dynamics within each of these states. We showed how one could use realizations
+  of any stochastic model like these in order to predict macroscopic flux and selectivity.
 
@@
   in order to analyze the MD trajectories and to hypothesize stochastic models which
-  matched the behavior of solutes.
-  \begin{itemize}
-    \item It would be significantly more useful and broadly applicable if we could 
-    design an approach which automatically distinguishes and parameterizes varied solute 
-    dynamics and leaves a facile way to generate an ensemble of stochastic trajectory
-    realizations that can be used to predict macroscopic transport properties.
-  \end{itemize}
-
-  In this work we attempt to minimize human effort by applying the infinite hidden 
-  Markov Model (IHMM)~\cite{beal_infinite_2002,calderon_inferring_2015}, a nonparameteric 
-  Bayesian classification technique, in order to automatically detect and infer the 
-  parameters of an unknown number of latent vector autoregressive (VAR) modes present 
-  in solute center-of-mass time series trajectories. 
-  \begin{itemize}
-    %MRS: start with where it has been used before (to establish utility) a
-    \item It's been used extensively for speaker diarization and has found some application
-    in single particle trajectory analysis.~\cite{calderon_inferring_2015,fox_sticky_2011}
-    %MRS: Then say it hasn't been used in this context (do we know of any, then cite, if none we have found, say so.)
-    \item The IHMM has not been used much for MD trajectory analysis.
+  matched the behavior of solutes. It would be significantly more useful and broadly 
+  applicable if we could design an approach which automatically distinguishes and 
+  parameterizes varied solute dynamics and leaves a facile way to generate an ensemble
+  of stochastic trajectory realizations that can be used to predict macroscopic transport
+  properties.
+
+  In this work we attempt to minimize human effort through a novel application of the 
+  the sticky hierarchical Dirichlet process autoregressive hidden markov model 
+  (HDP-AR-HMM), nonparameteric Bayesian classification technique that allows us to 
+  automatically detect and infer the parameters of an unknown number of latent vector
+  autoregressive (VAR) modes present in solute center-of-mass time series 
+  trajectories.~\cite{fox_bayesian_2010} The sticky HDP-AR-HMM greatly extends the 
+  basic framework of more limited finite hidden Markov modeling approaches.
+
+  In their most basic form, hidden Markov models (HMMs) are used to generate
+  a series of latent, or hidden, states dependent only on the previous state.~\cite{rabiner_tutorial_1989}
+  Propagating an HMM generates sequential but independent observations from 
+  the emission distributions associated with each hidden state. Transitions 
+  between states are mathematically defined by a matrix of transition probabilities.
+  Given a series of observations and a known number of hidden states, the 
+  Baum-Welch algorithm is the most commonly used way to determine the hidden
+  state sequence and the underlying parameters of a standard HMM.~\cite{baum_maximization_1970}
+  It also possible to achieve the same results using a Bayesian 
+  framework.~\cite{scott_bayesian_2002,jasra_markov_2005} One can place priors
+  on the transition probabilities and parameters of the hidden states' emission
+  distributions in order to iteratively infer their values and to estimate the hidden state
+  sequence. HMMs have been used in a broad range of applications including speech
+  recognition, weather forecasting and bioinformatics.~\cite{juang_on_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}
+  %BJC4: comment on usage in MD simulations. MSMs?
+
+  By placing a hierarchical Dirichlet process (HDP) prior on the transition 
+  probabilities, it is possible to extend HMMs to an unknown number of hidden
+  states.~\cite{teh_hierarchical_2006}
+  \begin{itemize}
+    \item We will refer to this as the HDP-HMM, although in literature it is 
+    often called the infinite hidden Markov model.~\cite{beal_infinite_2002}
+    \item The HDP-HMM elegantly overcomes the main shortcoming of standard
+    HMMs, the need to choose the number of states, making its use more 
+    advantageous in a diversity of applications.
+    \item
+
+    diverse applicability and improvement upon the shortcoming 
+    of standard HMMs
+    \item Applications...speaker diarization, etc.
+  \end{itemize}
+
+  One issue with the original formulation of HDP-HMM, is that it does not 
+  distinguish self-transitions and transitions between different states.
+  \begin{itemize}
+    \item Practically, this can result in rapid switching between states and
+    inferred state sequence representations that do a poor job of describing
+    the observations. 
+    \item Fox et al. addressed this issue by adding a `sticky' parameter.~\cite{fox_sticky_2007}
+    \item The sticky HDP-HMM is useful in situations where the user has
+    prior knowledge that state persistence is likely.
+    \item This is important for our work where we expect state persistence 
+    due to trapping.
+    \item Applications: Speaker diarization, SPT (Chris' diffusion papers)
+  \end{itemize}
+
+  The usefulness of the sticky HDP-HMM has been further extended to include 
+  temporal dependencies common to many real datasets.
+  \begin{itemize}
+    \item Fox et al. showed how to incorporate Markov jump linear systems (MJLSs)
+    into infinite state models.~\cite{fox_nonparameteric_2009}
+    \item An MJLS models each dynamical mode as a linear dynamical process.
+    \item There are two MJLS classes: switching linear dynamical systems (SLDSs) 
+    and switching vector autoregressive (VAR) processes.
+    \item Switching VAR processes are similar to SLDSs except that they do not
+    incorporate measurement noise.
+    \item Since MD simulations do not contain measurement noise, we will model
+    describe the dynamical modes exhibited by solutes in our MD simulations as 
+    VAR processes and we will refer to our model as an application of the 
+    HDP-AR-HMM, maintaining a distinction from HDP-SLDS models which can
+    be useful for experimental measurement where there is measurement noise.
+  \end{itemize}
+
+  To our knowledge, this is a novel application of the HDP-AR-HMM.
+  \begin{itemize}
+    \item We use the temporally-correlated parameters of the model in order
+    to learn physical mechanisms and describe solute kinetics.
+    \item We go beyond the typical application of IHMMs.
   \end{itemize}
@@
   \subsection{Predicting Mean Squared Displacement}\label{method:realizations}
-
+  %BJC4: reworked this section
   \textit{Generating Stochastic IHMM Trajectory Realizations}: We used two 
@@
 
+  %BJC4: new section below
   \subsection{Predicting Selectivity}\label{method:selectivity}
@@
 
-  %BJC4: It might be good to add a panel to this figure which gives a radial view of the pore
   \begin{figure}
@@
 
-%BJC4: the following has pretty all been replaced.
-%  Most of what we 
-%  have learned thus far has been based on the parameters of our model with some 
-%  qualitative validation using a single methanol trajectory. While 
-%  we may be able to further corroborate our arguments by analyzing more
-%  individual trajectories, it is more useful to correlate the state behavior with
-%  solute-membrane interactions.
-%
-%  %BJC2: A lot of the following will probably be reworked with different clustering scheme
-%%  \textit{Hydrogen Bonding Patterns}: 
-%  The types of hydrogen bonding undergone by solutes is dependent on radial
-%  location (see Figure~\ref{fig:hbond_pichart}). States with radial means near 1 nm
-%  or less (states 1, 3 and 5) typically hydrogen bond with the monomer carboxylate
-%  groups and ether linkages. States with radial means greater than 1 nm (states 2,
-%  4, 6 and 7) tend to hydrogen bond with the monomer tails. Our previous work has
-%  shown that there is a gradual transition from the hydrophilic to hydrophobic region in
-%  these membranes, meaning the monomer location is not tightly bound in $r$. 
-%  %MRS: above logic is not clear?
-%  Therefore, there are instances of hydrogen bond interactions that one might consider 
-%  uncharacteristic based on the state's radial mean.
-%  %MRS: what is implication of ``uncharacteristicness''? 
-%
-%  States which exhibit longer dwell times have longer hydrogen bond lifetimes (see
-%  Figure~\ref{fig:hbond_pichart}). States 3--7 have significantly longer hydrogen 
-%  bond lifetimes than states 1 and 2. It makes physical and mathematical sense that
-%  states 1 and 2 should not stay trapped by hydrogen bonding for long periods because
-%  they typically take large hops as communicated by their large covariances.
-%  In the tail states, hydrogen bond lifetimes appear to increase with their dwell 
-%  times. However, in the pores, the same linear relationship does not hold.
-%  For example, state 5 has the lowest hydrogen bond lifetime of states 3--7
-%  despite having the second longest dwell times.
-
-%  The local density experienced by solutes may have an impact on the length of solute 
-%  entrapment. On average, solutes in state 5 are surrounded by a relatively high density
-%  of particles. Based on its radial location and preference towards hydrogen bonding
-%  with the ether linkages (see Figure~\ref{fig:hbond_pi_charts}), it is reasonable to
-%  assume that while in state 5, methanol spends most of its time just outside the 
-%  pore region, sandwiched between the monomer head groups. Although state 5 hydrogen
-%  bonds break more frequently than one might expect for a state with long dwell times,
-%  it is possible that the solute's dense surroundings prevent it from wandering off 
-%  before the hydrogen bonding interaction can be recovered. This may explain the 
-%  behavior of the methanol in state 5 of the trajectory in Figure~\ref{fig:mechanism_map}
-%  where the solute's center of mass appears to move more freely about its mean than 
-%  other trapped states. The data suggests that methanol molecules in state 3 lie closer
-%  to the pore center than state 5 because they tend to hydrogen bond most frequently 
-%  with the carboxylate groups. Methanol molecules which experience state 3 are subject 
-%  to a lower density local environment and rely more heavily on hydrogen bonding interactions, 
-%  evidenced by their longer lifetimes, to stay trapped.
-%  
-%  States describing behavior in the tail region show a direct relationship between 
-%  hydrogen bond lifetimes and local density. Methanol molecules which experience state 2 
-%  spend their time in a low density region of the tails where they can easily break free
-%  of hydrogen bonds. Conversely, methanol molecules trapped in state 7 are in the densest 
-%  region of all states studied. It is likely difficult for methanol to escape these high 
-%  density regions and its position is further stabilized via hydrogen bonding.
-%  
-%  %BJC: I didn't put sodium ion association in this figure because it's infrequent. 
-%  %BJC: If I compare to acetic acid or urea, I could add it back. I was thinking of splitting
-%  % the pi chart in half with slices corresponding to hbonds on one side and association on the other
-%  \begin{figure}
-%  \centering
-%  \begin{subfigure}{0.54\textwidth}
-%  \includegraphics[width=\textwidth]{hbond_pi_charts.pdf}
-%  \caption{}\label{fig:hbond_pi_charts}
-%  \end{subfigure}
-%  \begin{subfigure}{0.45\textwidth}
-%  \includegraphics[width=\textwidth]{hbond_lifetimes_density_MET.pdf}
-%  \caption{}\label{fig:hbond_lifetimes_density_MET}
-%  \end{subfigure}
-%  %MRS: legend doesn't show stripes.
-%  \caption{(a) Methanol hydrogen bonds in different segments of the LLC monomer
-%  dependent on the state. States with mean radial locations in the pore region tend to
-%  hydrogen bond with the head groups and ether linkages. States with mean radial
-%  locations in the tails tend to hydrogen bond with the tail oxygen atoms.
-%  (b) Hydrogen bond lifetimes and the local density experienced by methanol
-%  molecules can help us to understand dynamical states in terms of membrane 
-%  interactions. The bars are colored according to match the states in Figures~\ref{fig:mechanism_map}
-%  and~\ref{fig:common_states_MET}. States 1 and 2, which have large covariances, also have short
-%  hydrogen bond lifetimes and exist in relatively low density regions. The
-%  hydrogen bond lifetimes of methanol in states with radial means in the tail
-%  region tend to increase with local density and mean dwell times. 
-%  %MRS7: not clear from graphic which ones are in the pore.
-%  %MRS7: is there any legend for the color for b? If same as above figure, indicate. Don't REALLY need color since they bars are already labeled, so it's 2 sources of duplicate information.
-%  %BJC7: The state numbers are all you need to compare to the previous figure BUT the color make it easier 
-%  %plot of the methanol trajectory where states aren't labeled.
-%  %MRS7: cross-hatching doesn't appear in the legend? Not sure which is which (I assume hatched is number density because closer to that axis).
-%  %BJC7: Is it because the hatches aren't dense enough? I see them in the legend
-%  This monotonic
-%  relationship does not exist for states in the pore region. The high 
-%  local density experienced by state 5 methanol molecules may explain why 
-%  hydrogen bond lifetimes are short but dwell times are high. State 5 methanol's
-%  preference towards hydrogen bonds with ether linkages suggests that the solute
-%  sits between LLC monomer head group which prevent it from wandering to far
-%  before recovering its previous hydrogen bond.
-%  }\label{fig:hbond_pichart}
-%  \end{figure}
-
   \subsubsection*{Comparison of Solute Behavior}

### 2020-05-15 Ben_Manuscripts/hdphmm/Draft.tex
New references and review of hmms

@@
   sequence. HMMs have been used in a broad range of applications including speech
-  recognition, weather forecasting and bioinformatics.~\cite{juang_on_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}
+  recognition, weather forecasting and bioinformatics.~\cite{juang_hidden_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}
   %BJC4: comment on usage in MD simulations. MSMs?
@@
   probabilities, it is possible to extend HMMs to an unknown number of hidden
-  states.~\cite{teh_hierarchical_2006}
-  \begin{itemize}
-    \item We will refer to this as the HDP-HMM, although in literature it is 
-    often called the infinite hidden Markov model.~\cite{beal_infinite_2002}
-    \item The HDP-HMM elegantly overcomes the main shortcoming of standard
-    HMMs, the need to choose the number of states, making its use more 
-    advantageous in a diversity of applications.
-    \item
-
-    diverse applicability and improvement upon the shortcoming 
-    of standard HMMs
-    \item Applications...speaker diarization, etc.
-  \end{itemize}
-
-  One issue with the original formulation of HDP-HMM, is that it does not 
-  distinguish self-transitions and transitions between different states.
-  \begin{itemize}
-    \item Practically, this can result in rapid switching between states and
-    inferred state sequence representations that do a poor job of describing
-    the observations. 
-    \item Fox et al. addressed this issue by adding a `sticky' parameter.~\cite{fox_sticky_2007}
-    \item The sticky HDP-HMM is useful in situations where the user has
-    prior knowledge that state persistence is likely.
-    \item This is important for our work where we expect state persistence 
-    due to trapping.
-    \item Applications: Speaker diarization, SPT (Chris' diffusion papers)
-  \end{itemize}
+  states.~\cite{teh_hierarchical_2006} We will refer to this as the HDP-HMM,
+  although in literature it is often called the infinite hidden Markov 
+  model.~\cite{beal_infinite_2002} The HDP-HMM elegantly overcomes the main
+  shortcoming of standard HMMs, the need to choose the number of states 
+  \textit{a priori}, making its use more advantageous in a diversity of 
+  applications including single particle trajectory analysis and economic 
+  data interpretation.~\cite{hines_analyzing_2015,shi_identifying_2016} 
+  This approach allows the complexity of the data to drive the complexity
+  of the model.
+
+  One issue with the original formulation of the HDP-HMM, is that it does 
+  not distinguish self-transitions and transitions between different states.
+  Practically, this can result in rapid switching between states and inferred
+  state sequence representations that do a poor job of describing the 
+  observations. Fox et al. addressed this issue by adding a `sticky' 
+  parameter.~\cite{fox_sticky_2007} The sticky HDP-HMM is useful in situations
+  where the user has prior knowledge that state persistence is likely.
+  For example, it is unlikely that a conversation between two people would 
+  rapidly switch between speakers.~\cite{fox_sticky_2011} This is also 
+  important for our work where we expect state persistence due to trapping.
 
   The usefulness of the sticky HDP-HMM has been further extended to include 
-  temporal dependencies common to many real datasets.
-  \begin{itemize}
-    \item Fox et al. showed how to incorporate Markov jump linear systems (MJLSs)
-    into infinite state models.~\cite{fox_nonparameteric_2009}
-    \item An MJLS models each dynamical mode as a linear dynamical process.
-    \item There are two MJLS classes: switching linear dynamical systems (SLDSs) 
-    and switching vector autoregressive (VAR) processes.
-    \item Switching VAR processes are similar to SLDSs except that they do not
-    incorporate measurement noise.
-    \item Since MD simulations do not contain measurement noise, we will model
-    describe the dynamical modes exhibited by solutes in our MD simulations as 
-    VAR processes and we will refer to our model as an application of the 
-    HDP-AR-HMM, maintaining a distinction from HDP-SLDS models which can
-    be useful for experimental measurement where there is measurement noise.
-  \end{itemize}
-
-  To our knowledge, this is a novel application of the HDP-AR-HMM.
-  \begin{itemize}
-    \item We use the temporally-correlated parameters of the model in order
-    to learn physical mechanisms and describe solute kinetics.
-    \item We go beyond the typical application of IHMMs.
-  \end{itemize}
-
+  temporal dependencies common to many real datasets. State dynamics and 
+  relaxation into new states are often correlated.~\cite{calderon_data-driven_2014}
+  Fox et al. showed formulated a method that accounts for this behavior by
+  incorporating Markov jump linear systems (MJLSs) into infinite state 
+  models.~\cite{fox_nonparametric_2009} An MJLS models each dynamical mode
+  as a linear dynamical process. Two MJLS sub-classes are switching linear
+  dynamical systems (SLDSs) and switching vector autoregressive (VAR) processes.
+  Switching VAR processes are similar to SLDSs except that they do not
+  incorporate measurement noise. Since MD simulations do not contain measurement
+  noise, we will model the dynamical modes exhibited by MD solute trajectories 
+  as VAR processes and we will refer to our model as an application of the 
+  sticky HDP-AR-HMM in order to maintaining its the even more general sticky
+  HDP-SLDS models.
+
+  To our knowledge, this is a novel application and analysis of the sticky 
+  HDP-AR-HMM. Typical applications center around determining the number of
+  states, the state sequence and occasional analysis of the emission 
+  distributions. The addition of temporal correlation to the inference 
+  procedure has primarily been used to improve state sequence 
+  identification.~\cite{calderon_inferring_2015,hamada_modeling_2016}
+  Not only do we use the HDP-AR-HMM to segment MD time series into distinct
+  dynamical modes, but we use temporally-correlated parameters of the model
+  in order to learn physical mechanisms and describe solute kinetics. 
+  %Further, we use the model parameters to generate new time series trajectories.
+
+  %BJC4: enumerate?
   We aim to address two primary scientific questions with this work:

### 2020-05-15 Ben_Manuscripts/hdphmm/Draft.tex
Improvements to methods

@@
   predicting bulk properties characteristic of much longer time scales. In this work 
-  we apply the infinite hidden Markov model (IHMM) to solute center-of-mass trajectories
-  generated from long molecular dynamics simulations in a cross-linked inverted hexagonal
-  phase lyotropic liquid crystal (LLC) membrane in order to automatically detect a
-  variety of solute dynamical states which can be further explained in terms of 
-  solute-membrane interactions.
-
-  We group the states identified by the IHMM into clusters based on multiple metrics
+  we apply the sticky hierarchical Dirichlet process hidden Markov model (HDP-AR-HMM) 
+  to solute center-of-mass trajectories generated from long molecular dynamics 
+  simulations in a cross-linked inverted hexagonal phase lyotropic liquid crystal 
+  (LLC) membrane in order to automatically detect a variety of solute dynamical states
+  which can be further explained in terms of solute-membrane interactions.
+
+  We group the states identified by the HDP-AR-HMM into clusters based on multiple metrics
   aimed at distinguishing solute behavior based on their fluctuations, dwell times
@@
 
-  Along with parameters of individual states, the IHMM simultaneously infers a transition
+  Along with parameters of individual states, the HDP-AR-HMM simultaneously infers a transition
   matrix which allows us to stochastically propagate solute behavior from all of the 
@@
   There is a need for highly selective membranes in order to perform efficient 
-  separations of the components of complex aqueous streams.
-  \begin{itemize}
-    \item Desalination and boric acid removal from seawater.
-    \item Organic micropollutants
-    \item Hydraulic fracturing flowback water
-    \item Breathable chemical warfare agent barriers
-    \item High purity chemicals
-    \item While many researchers focus on membrane permeability, we may be 
-    able to reduce costs of commercial nanofiltration and reverse osmosis with
-    higher selectivity.~\cite{werber_materials_2016}
-  \end{itemize}
+  separations of the components of complex aqueous streams. Seawater and
+  bracksih water desalination, separation of organic micropollutants from 
+  municipal water supplies, recovering valuable dissolved species from 
+  waste stream and creating breathable barriers to harmful contaminants are just a
+  subset of the broad range of applications for selective membrane separations.~\cite{fritzmann_state---art_2007,fonseca_couto_critical_2018,dischinger_evaluation_2019,ramaseshan_functionalized_2006}
+  While researchers often focus on membrane permeability, many argue that
+  it may be more beneficial to focus on membrane selectivity in order to 
+  reduce the costs of commercial nanofiltration and reverse osmosis.~\cite{werber_materials_2016}
 
@@
   easily bridge the disconnect between theory and application. In many systems, it's 
-  possible to achieve this by calculating diffusion constants. Unfortunately, for 
+  possible to achieve this by calculating diffusion constants. 
+  % BJC4: even if we could calculate diffusion constants, wouldn't there still be value 
+  % in understanding chemical detail?
+  % BJC4: It might not be a good idea to blame our need for this modeling on non-linear MSDs, 
+  % especially since our MSDs appear to be at or nearing a linear regime.
+  % BJC4: seems like we should be addressing the problem as short time scale subdiffusive 
+  % dynamics that dictates measureable long time scale diffusion. Although curves become linear,
+  % the slopes should be a product of the short time scale motion.
+  Unfortunately, for 
   systems which exhibit complex short timescale subdiffusive dynamics, one cannot 
-  calculate reliably compute diffusion constants since solute mean square 
+  reliably compute diffusion constants since solute mean square 
   displacements (MSDs) are non-linear on the timescales accessible to molecular simulation.
@@
 
-  In this work we attempt to minimize human effort through a novel application of the 
-  the sticky hierarchical Dirichlet process autoregressive hidden markov model 
-  (HDP-AR-HMM), nonparameteric Bayesian classification technique that allows us to 
+  In this work we attempt to minimize human effort through a novel application of 
+  the sticky hierarchical Dirichlet process autoregressive hidden Markov model 
+  (HDP-AR-HMM), a nonparameteric Bayesian classification technique that allows the user to 
   automatically detect and infer the parameters of an unknown number of latent vector
-  autoregressive (VAR) modes present in solute center-of-mass time series 
-  trajectories.~\cite{fox_bayesian_2010} The sticky HDP-AR-HMM greatly extends the 
-  basic framework of more limited finite hidden Markov modeling approaches.
+  autoregressive (VAR) modes present in solute center-of-mass MD 
+  trajectory.~\cite{fox_bayesian_2010} The sticky HDP-AR-HMM greatly extends the 
+  basic framework of simpler but more limited finite hidden Markov modeling approaches.
 
@@
   sequence. HMMs have been used in a broad range of applications including speech
-  recognition, weather forecasting and bioinformatics.~\cite{juang_hidden_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}
-  %BJC4: comment on usage in MD simulations. MSMs?
+  recognition, weather forecasting and bioinformatics.~\cite{juang_hidden_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}. In molecular simulations, HMMs have been
+  used to characterize molecular kinetics in order to determine the equilibrium 
+  distribution of various observables.~\cite{noe_probability_2008}
 
@@
   probabilities, it is possible to extend HMMs to an unknown number of hidden
-  states.~\cite{teh_hierarchical_2006} We will refer to this as the HDP-HMM,
+  states, thus allowing the model's complexity to be driven by the complexity
+  of the data.~\cite{teh_hierarchical_2006} We will refer to this as the HDP-HMM,
   although in literature it is often called the infinite hidden Markov 
@@
   \textit{a priori}, making its use more advantageous in a diversity of 
-  applications including single particle trajectory analysis and economic 
-  data interpretation.~\cite{hines_analyzing_2015,shi_identifying_2016} 
-  This approach allows the complexity of the data to drive the complexity
-  of the model.
+  applications including economic data and single particle trajectory 
+  analysis.~\cite{shi_identifying_2016,hines_analyzing_2015}
 
@@
   where the user has prior knowledge that state persistence is likely.
-  For example, it is unlikely that a conversation between two people would 
-  rapidly switch between speakers.~\cite{fox_sticky_2011} This is also 
-  important for our work where we expect state persistence due to trapping.
+  For example, in the case of speaker diarization, it is unlikely that a 
+  conversation between two people would rapidly switch between speakers.~\cite{fox_sticky_2011}
+  This is also important for our work where we expect state persistence due
+  to solute entrapment.
 
@@
   relaxation into new states are often correlated.~\cite{calderon_data-driven_2014}
-  Fox et al. showed formulated a method that accounts for this behavior by
+  Fox et al. formulated a method that accounts for this behavior by
   incorporating Markov jump linear systems (MJLSs) into infinite state 
@@
   as VAR processes and we will refer to our model as an application of the 
-  sticky HDP-AR-HMM in order to maintaining its the even more general sticky
-  HDP-SLDS models.
+  sticky HDP-AR-HMM in order to maintaining its distinction from the even more
+  general sticky HDP-SLDS models.
 
@@
   Not only do we use the HDP-AR-HMM to segment MD time series into distinct
-  dynamical modes, but we use temporally-correlated parameters of the model
-  in order to learn physical mechanisms and describe solute kinetics. 
-  %Further, we use the model parameters to generate new time series trajectories.
+  dynamical modes, but we cluster and analyze the temporally-correlated 
+  parameters of the model in order to learn physical mechanisms and describe
+  solute kinetics. Further, we use the model parameters to generate new 
+  time series trajectories which enable projections of MD simulations on 
+  much longer time scales.
 
   %BJC4: enumerate?
+  %BJC4: might be able to condense this since some of it repeats above.
   We aim to address two primary scientific questions with this work:
-  First, we want to know whether it is possible to predict macroscopic transport
-  properties. We use the VAR parameters and state transition probability matrix of
-  the IHMM in order to generate stochastic trajectory realizations with behavior 
-  similar to that exhibited by MD. One can project these realizations onto much 
-  longer timescales with computational ease extending into timescales where 
+  First, we want to know whether it is possible to use the HDP-AR-HMM to 
+  help us predict macroscopic transport properties. We use the VAR parameters
+  and state transition probability matrix of the HDP-AR-HMM in order to 
+  generate stochastic trajectory realizations with behavior similar to that
+  exhibited by MD. One can project these realizations onto much longer 
+  timescales with computational ease extending into timescales where 
   regular diffusive behavior again occurs.
-  Second, we want to know if the IHMM algorithm can help researchers
+  Second, we want to know if the HDP-AR-HMM algorithm can help researchers
   efficiently uncover underlying transport mechanisms which give rise to different 
   solute dynamical behavior.
-  We use the parameters of the states identified by the IHMM in order to infer 
+  We use the parameters of the states identified by the HDP-AR-HMM in order to infer 
   dominant solute-membrane interactions and transport mechanisms. We cluster similar 
@@
   ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}  
-  Our python implementation of the IHMM algorithm is available online at \\
+  Our python implementation of the HDP-AR-HMM algorithm is available online at \\
   \texttt{https://github.com/bencoscia/hdphmm}. All other post-simulation 
@@
   relatively diverse set of chemical functionality. For each solute we created a 
-  separate system and to 
-  each system we added 6 solutes per pore for a total of 24 solutes. This number 
+  separate system and to each system we added 6 solutes per pore for a total of 24 solutes. This number 
   of solutes per pore provides a balance of a low degree of interaction between 
@@
 
-  \subsection{The Infinite State Hidden Markov Model}\label{method:IHMM}
-
-  %BJC2: I left section numbers off
-  \subsubsection*{Extending Hidden Markov Modeling to an Unknown Number of States}
-
-  Hidden Markov models (HMMs) are a useful and widely used technique for modeling
-  sequences of observations where the probability of the next observation in a 
-  sequence depends, at least in part, on a previous unobserved, latent or hidden,
-  state.~\cite{beal_infinite_2002} In the context of our simulations, the observations
-  correspond to the center of mass coordinates of the solutes versus time, and the
-  states correspond to segments of the trajectory with similar dynamical behavior 
-  which gives rise to those types of observations. The probability of transitioning 
-  to a state based on the current state is defined in terms of an $n\times n$ 
-  transition probability matrix, $T$, where $n$ is the number of states. Unfortunately,
-  standard HMMs require $n$ to be known \textit{a priori}. One can partially overcome
-  this by testing a range of numbers of hidden states and determining which is the
-  best representation of the data.~\cite{pohle_selecting_2017}
-
-  The infinite-state HMM overcomes this drawback by placing a hierarchical
-  Dirichlet process (HDP) prior on the transition probabilities.~\cite{fox_bayesian_2010} Using some 
-  base probability distribution, $H$, a Dirichlet process (DP) generates discrete 
-  distributions, $G_0$, over a countably infinite number of probability measures:
-  \begin{equation}
-      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
-  \end{equation}
-  where the $\theta_k$ are values drawn from the base distribution and the weights
-  $\beta_k$ come from a stick-breaking process parameterized by the concentration 
-  parameter $\gamma$ (equivalently referred to as GEM($\gamma$)).~\cite{halmos_random_1944} In shorthand, this
-  specification can be expressed as $G_0 \sim DP(\gamma, H)$. The concentration 
-  parameter, $\gamma$, expresses one's confidence in the base distribution $H$.
-  We use a uniform base distribution for $H$. When $\gamma\to 0$, the first 
-  weight of $G_0$, $\beta_1$, approaches unity and for $\gamma\to\infty$, the weights
-  become uniform and $G_0$ closely resembles $H$. Each row, $G_j$, of the transition 
-  matrix is produced by drawing from a DP specified using the $\beta$ vector as a 
-  discrete base distribution and a separate concentration parameter, $\alpha$.
-  \begin{equation}
-      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
-  \end{equation}
-  This hierarchical specification ensures that the transition probabilities in 
-  each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
-  Once the model has converged only a finite number of states will have significant
-  sampling.
-
-  \subsubsection*{Parameterizing the Hidden States}\label{method:var_params}
-
-  We describe the dynamics of each state visited by solutes in our MD simulations using
-  a first order vector autoregressive (VAR(1)) model. In general, a VAR($r$) process is characterized by a
+  \subsection{Applying the sticky HDP-AR-HMM to MD Trajectories}\label{method:HDP-AR-HMM}
+
+  % BJC4: Chris' general comment for this section: 'the problem with this section is 
+  % that it doesn't help the expert or novice figure out what is being done (either 
+  % expand more or relegate details to references and talk bigger picture)'
+
+  % BJC4: I think it makes sense to stick to bigger picture since there are much
+  % better descriptions in literature. I haven't made any modifications to what's already been done
+
+  % BJC4: replaced with what follows. Lots of the big picture is in the intro
+
+%  \subsubsection*{Extending Hidden Markov Modeling to an Unknown Number of States}
+%  
+%  Hidden Markov models (HMMs) are a useful and widely used technique for modeling
+%  sequences of observations where the probability of the next observation in a 
+%  sequence depends, at least in part, on a previous unobserved, latent or hidden,
+%  state.~\cite{beal_infinite_2002} In the context of our simulations, the observations
+%  correspond to the center of mass coordinates of the solutes versus time, and the
+%  states correspond to segments of the trajectory with similar dynamical behavior 
+%  which gives rise to those types of observations. The probability of transitioning 
+%  to a state based on the current state is defined in terms of an $n\times n$ 
+%  transition probability matrix, $T$, where $n$ is the number of states. Unfortunately,
+%  standard HMMs require $n$ to be known \textit{a priori}. One can partially overcome
+%  this by testing a range of numbers of hidden states and determining which is the
+%  best representation of the data.~\cite{pohle_selecting_2017}
+%  
+%  The infinite-state HMM overcomes this drawback by placing a hierarchical
+%  Dirichlet process (HDP) prior on the transition probabilities.~\cite{fox_bayesian_2010} Using some 
+%  base probability distribution, $H$, a Dirichlet process (DP) generates discrete 
+%  distributions, $G_0$, over a countably infinite number of probability measures:
+%  \begin{equation}
+%      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
+%  \end{equation}
+%  where the $\theta_k$ are values drawn from the base distribution and the weights
+%  $\beta_k$ come from a stick-breaking process parameterized by the concentration 
+%  parameter $\gamma$ (equivalently referred to as GEM($\gamma$)).~\cite{halmos_random_1944} In shorthand, this
+%  specification can be expressed as $G_0 \sim DP(\gamma, H)$. The concentration 
+%  parameter, $\gamma$, expresses one's confidence in the base distribution $H$.
+%  We use a uniform base distribution for $H$. When $\gamma\to 0$, the first 
+%  weight of $G_0$, $\beta_1$, approaches unity and for $\gamma\to\infty$, the weights
+%  become uniform and $G_0$ closely resembles $H$. Each row, $G_j$, of the transition 
+%  matrix is produced by drawing from a DP specified using the $\beta$ vector as a 
+%  discrete base distribution and a separate concentration parameter, $\alpha$.
+%  \begin{equation}
+%      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
+%  \end{equation}
+%  This hierarchical specification ensures that the transition probabilities in 
+%  each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
+%  Once the model has converged only a finite number of states will have significant
+%  sampling.
+
+  We use the sticky HDP-AR-HMM in order to assign the time-correlated positional 
+  fluctuations of solute center-of-mass MD trajectories to discrete dynamical modes while 
+  simultaneously inferring the VAR parameters of those modes. We use the sticky model
+  in order to emphasize self-transitions since we expect solutes to stay trapped in
+  states for appreciable amounts of time. We analyze solute motion in terms of their
+  cylindrical coordinates, $(r, z)$, with the $z$ axis oriented along the membrane 
+  pores and the radial dimension, $r$, measured from the closest pore center.
+
+  Although the discussion will be presented in terms of 2D cylindrical coordinates, we
+  applied the HDP-AR-HMM algorithm to 3D solute center-of-mass coordinate trajectories 
+  with the radial dimension represented by the solute's $x$ and $y$ coordinates 
+  transformed relative to the nearest pore center. By working in Cartesian coordinates,
+  we avoid mathematical complexity introduced by change of coordinates into cylindrical
+  coordinates while estimating the state sequence.
+
+  We implemented the sticky HDP-AR-HMM in Python 
+  (\texttt{https://github.com/bencoscia/hdphmm}) which we heavily adapted from
+  the MATLAB code of Fox et al.~\cite{fox_nonparametric_2009} Since we do not incorporate
+  any novel methodology to the HDP-AR-HMM inference procedure, we refer the 
+  interested reader to an excellent and in-depth description of the formulation of
+  the HDP-AR-HMM and related models.~\cite{fox_bayesian_2010}
+
+  %\subsubsection*{Parameterizing the Hidden States}\label{method:var_params}
+  \textit{Parameterizing the Hidden States}: We describe the dynamics of each 
+  state visited by solutes in our MD simulations using a first order vector 
+  autoregressive (VAR(1)) model. In general, a VAR($r$) process is characterized by a
   vector of observations in a time series that are linearly dependent on $r$ previous
@@
   This means that we only parameterize $A_1$. To simplify notation, we will just
-  call it $A$. We used a matrix-normal inverse-Wishart prior on parameters $A$ and 
-  $\Sigma$ and a Gaussian prior on $\mathbf{c}$ in order to infer their 
+  call it $A$. We used conjugate matrix-normal inverse-Wishart (MNIW) prior on parameters 
+  $A$ and $\Sigma$ and a Gaussian prior on $\mathbf{c}$ in order to infer their 
   values.~\cite{fox_nonparametric_2009}
 
-  \subsubsection*{Applying the IHMM to MD Trajectories}
-
-  Using the IHMM framework, we estimated the most likely sequence of hidden states in
-  each solute center-of-mass trajectory while simultaneously inferring VAR(1)
-  parameters for each state and the overall state transition probability matrix, $T$.
-  We created a Python implementation of this process 
-  (\texttt{https://github.com/bencoscia/hdphmm}) which we heavily adapted from
-  the MATLAB code of Fox et al.~\cite{fox_bayesian_2010} Parameter estimation is iterative. 
-  %MRS2: give location for the code here where you introduce it.
-  %BJC3: I emailed Emily Fox and she just asked me to use this citation. I'm happy to add a 
-  %link to where she stores the code. Would that be best in the form of a reference?
-  %MRS3: I was thinking of citing YOUR code here.
-  %BJC4: Ah, OK. I plan to fork it into the shirtgroup repo after we submit. Can change link after reviews.
-  %BJC4: Okay to put link? Or should I cite it as a reference?
-  Therefore, we looked for convergence of the parameters in Equation~\ref{eqn:var}.
-  We detected equilibration of the parameters using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
-  on the time series of parameter estimates. Plots illustrating parameter convergence are 
-  available in Section~\ref{S-section:convergence} of the Supporting Information. We 
-  refer the interested reader to much more extensive descriptions of the inference and 
-  sampling procedures used to estimate the VAR(1) parameters and the state sequence. ~\cite{beal_infinite_2002,teh_hierarchical_2006,van_gael_beam_2008,fox_nonparametric_2009,fox_bayesian_2010}
-
-  We start by applying the IHMM algorithm to the 3D solute center-of-mass coordinate 
-  trajectories transformed relative to the closest pore center. We tracked the solute's
-  motion along the pore axis with the center-of-mass $z$ coordinate. Using the nearest
-  pore center as the origin, we represented the radial distance of each solute's 
-  center-of-mass from the pore center in 2 dimensions, $x$ and $y$. By working in 
-  Cartesian coordinates, we avoid mathematical complexity introduced by change of 
-  coordinates into cylindrical coordinates while estimating the state sequence.
-
-  We parameterized each of the 24 solute trajectories independently.
-  Although the IHMM is capable of identifying an infinite number of states, 
+%  \subsubsection*{Applying the HDP-AR-HMM to MD Trajectories}
+
+  \textit{State sequence and parameter inference}: We inferred the 
+  state sequence and parameters for each of the 24 solute trajectories independently.
+  Although the HDP-AR-HMM is capable of identifying an infinite number of states, 
   a Dirichlet process tends to exhibit a ``rich get richer" effect, favoring
@@
   similar states which we would prefer to stay separated before clustering.
-  Note that the states identified by the IHMM are heavily influenced by 
-  the Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. 
-  In Section~\ref{S-section:prior_guesses} of the Supporting Information we 
-  outline our method for choosing reliable prior parameters.
-
-  We ran 2000 iterations of the IHMM procedure in order to arrive at converged 
-  state sequences. We evaluated the convergence of the state sequence based on
-  the convergence of the VAR parameters. The parameters of each state
-  generally converge within 500--1000 iterations. However, the boundaries of 
-  each state segment fluctuate which can lead to high variance in the $A$
-  and $\Sigma$ parameters in segments with a relatively low number of emissions.
-  In these cases, plateauing of the mean in each dimension tends to be a more 
-  reliable indicator of convergence (see Figure~\ref{S-fig:convergence3d} of
-  the Supporting Information).
-
-%  It is important not to view the IHMM as a black box. One should verify that the
-%  model produces qualitative and quantitative results that are accurate on a
-%  trajectory-by-trajectory basis.
-%  \begin{itemize}
-%    \item If the state sequence is not properly partitioned it can lead to 
-%    poor estimates of the transition matrix.
-%    \item In the supporting information, we demonstrate this and provide techniques
-%    for ensuring good state partitioning.
-%  \end{itemize}
+
+  We ran 2000 iterations of the HDP-AR-HMM procedure on each trajectory which
+  was sufficient in order to arrive at converged state sequences and VAR parameter
+  estimates. By our criteria, the procedure generally converged within 500--1000 iterations. We 
+  evaluated convergence based on when the VAR parameter estimates plateaued. 
+  We detected plateaus using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
+  on the time series of the individual parameters (Section~\ref{S-section:convergence}
+  of the Supporting Information). Convergence of the VAR parameters implies that
+  the state sequence is relatively stable since the inferred parameters are 
+  sensitive to the inputs to the MNIW conjugate priors. In states with a low number
+  of emissions, the boundaries of the state segments fluctuate which can lead to high
+  variance in the $A$ and $\Sigma$ parameters. In these cases, plateauing of the mean in each dimension 
+  tends to be a more reliable indicator of convergence (see 
+  Figure~\ref{S-fig:convergence3d} of the Supporting Information).
+
+  It is usually beneficial to employ intelligent state sequence initialization procedures. 
+  Most importantly, states identified by the HDP-AR-HMM are heavily influenced by the 
+  Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. In 
+  Section~\ref{S-section:prior_guesses} of the Supporting Information we outline our 
+  algorithmic method for choosing reliable prior parameters. We provide additional 
+  practical tips for initialization in Section~\ref{S-section:fitting_tips}
+  of the Supporting Information.
 
@@
 
-  We reduced the parameter space used agglomerative clustering, a hierarchical
+  We reduced the parameter space using agglomerative clustering, a hierarchical
   clustering approach which uses a linkage criteria in order to successively merge
@@
   rather than the distance threshold. For our data, non-parametric methods such as 
-  Bayesian Gaussian mixture models~\cite{pedregosa_scikit-learn_2011,gelman_bayesian_2013}
+  Dirchlet process Gaussian mixture models~\cite{pedregosa_scikit-learn_2011,gelman_bayesian_2013}
   tend to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
@@
   \begin{equation}  
-   E[dwell time] = \frac{1}{1 - T_{ii}}
+   E[dwell~time] = \frac{1}{1 - T_{ii}}
    \label{eqn:dwell_times}
@@
   clusters but may result in a large number of them. Once one has achieved a better 
-  understanding of solute-membrane interactions, perhaps by using the iHMM, it may be
+  understanding of solute-membrane interactions, perhaps by using the HDP-AR-HMM, it may be
   beneficial to incorporate other physically motivated variables into the clustering
@@
 
-  \subsubsection*{Choosing the Number of Clusters}
-
-  Choosing the number of clusters can be somewhat subjective so we attempted to add some
-  structure to the selection process by following a set of qualitative and quantitative 
-  guidelines. We give an in depth justification of our clustering choices in 
-  Section~\ref{S-section:nclusters} of the Supporting Information. We used the silhouette
+  %\subsubsection*{Choosing the Number of Clusters}
+
+  \textit{Choosing the Number of Clusters}: To aid interpretation, our goal was to
+  use the lowest number of clusters that adequately distinguished the dynamics of 
+  each solute, which requires careful consideration of the data. We used the silhouette
   test in order to score the quality of clustering as a function of the number of clusters
@@
   distinguish between visually obvious differences in dynamic behavior. This can result 
-  in finalized parameter sets that are averages of distinct behavior which presents 
-  further problems with the predictive modeling that we discuss later on.
-
-  %BJC4: added
-  We aimed to maintain the highest silhouette score, and thus lowest number of clusters,
-  possible while preserving the dynamics of each trajectory.
-  %verifying that visually distinct states stayed separated. 
-  We verified preservation of the dynamics by comparing the MSDs of stochastic trajectory
-  realizations based on clustered IHMM parameter sets to the pooled MSDs of stochastic 
-  realizations of IHMMs fit to individual trajectories (see Section~\ref{method:realizations}).
-  We chose the lowest number of clusters that reasonably reproduced the pooled MSDs at 
-  short and long time lags (See Figure~\ref{S-fig:MET_nclusters} of the Supporting 
-  Information).
-
-  \subsubsection*{Obtaining Parameters of Clustered States}
+  in finalized parameter sets that are averages of distinct behavior. Since choosing 
+  the number of clusters depends on user-selected criteria, we give an in depth 
+  justification of our approach to choosing the number of clusters in 
+  Section~\ref{S-section:nclusters} of the Supporting Information.
+
+%  We aimed to maintain the highest silhouette score, and thus lowest number of clusters,
+%  possible while preserving the dynamics of each trajectory.
+%  %verifying that visually distinct states stayed separated. 
+%  We verified preservation of the dynamics by comparing the MSDs of stochastic trajectory
+%  realizations based on clustered HDP-AR-HMM parameter sets to the pooled MSDs of stochastic 
+%  realizations of HDP-AR-HMMs fit to individual trajectories (see Section~\ref{method:realizations}).
+%%  We chose the lowest number of clusters that reasonably reproduced the pooled MSDs at 
+%%  short and long time lags (See Figure~\ref{S-fig:MET_nclusters} of the Supporting 
+%%  Information).
+
+  %\subsubsection*{Obtaining Parameters of Clustered States}
 
   %BJC3: modified 
-
-  We remapped and fixed the state sequence based on the cluster assignments and 
-  parameterized the clusters using the inference component of the IHMM algorithm.
+  \textit{Obtaining Parameters of Clustered States}: We remapped and fixed the
+  state sequence based on the cluster assignments and 
+  parameterized the clusters using the inference component of the HDP-AR-HMM algorithm.
   First, we modified the ($x$, $y$, $z$) solute trajectories so that they had a 
@@
   and $z$ dimensions, with the mean in $y$ being zeroed by the rotation. We used
-  the inference component of the IHMM algorithm on this modified trajectory to 
+  the inference component of the HDP-AR-HMM algorithm on this modified trajectory to 
   infer the clustered state parameters by fixing the clustered state sequence.
@@
   %BJC4: reworked this section
-  \textit{Generating Stochastic IHMM Trajectory Realizations}: We used two 
+  \textit{Generating Stochastic HDP-AR-HMM Trajectory Realizations}: We used two 
   different methods to stochastically generate trajectories:
@@
     \item For each independent MD trajectory, we generated stochastic trajectory
-    realizations using the finalized parameters of the associated IHMM. This 
+    realizations using the finalized parameters of the associated HDP-AR-HMM. This 
     results in 24 separate ensembles of trajectories for each solute studied. 
@@
   For both approaches, we drew state sequences with transition probabilities given 
-  by $T$ of the IHMM. While in a given state, we simulated motion according to the 
+  by $T$ of the HDP-AR-HMM. While in a given state, we simulated motion according to the 
   VAR(1) parameterization of that state. After each state transition, we set the 
@@
   	\item For each trial, we generated 24 stochastic trajectories, one from each of
-  	the 24 independent IHMM models. The result of the bootstrap trial is the mean
+  	the 24 independent HDP-AR-HMM models. The result of the bootstrap trial is the mean
   	of the MSDs calculated from each trajectory. 
@@
 
-  \textit{Expected dwell times}:
-
   \textit{Hydrogen bond detection}: We determined the number of hydrogen bonds 
@@
 
-  We applied the IHMM independently to all 24 trajectories of each of the four solutes studied.
+  We applied the HDP-AR-HMM independently to all 24 trajectories of each of the four solutes studied.
   The number of states found for each trajectory varied between 5 and 30.  %BJC4: MET: (5, 28), need to finalized
-  In Figure~\ref{fig:rz_unclustered}, we show the state sequence determined by the IHMM for
+  In Figure~\ref{fig:rz_unclustered}, we show the state sequence determined by the HDP-AR-HMM for
   an example methanol trajectory. The model distinguishes many of the states due to 
@@
   \includegraphics[width=\textwidth]{rz_unclustered_MET.pdf}
-  \caption{The IHMM found 24 distinct VAR(1) states in this representative methanol trajectory.
+  \caption{The HDP-AR-HMM found 24 distinct VAR(1) states in this representative methanol trajectory.
   We performed the parameterization in 3D cartesian coordinates, but for this figure, we 
@@
 
-  \subsection{Reproducing MD Trajectories and MSDs with the IHMM}\label{section:unclustered_MSD_prediction}
+  \subsection{Reproducing MD Trajectories and MSDs with the HDP-AR-HMM}\label{section:unclustered_MSD_prediction}
 
   Before analyzing solute behavior characteristic to the states identified by the
-  IHMM, it is important to verify whether the state dynamics are consistent with MD
+  HDP-AR-HMM, it is important to verify whether the state dynamics are consistent with MD
   both qualitatively and quantitatively. Therefore, we generated stochastic 
@@
   \includegraphics[width=\textwidth]{qualitative_unclustered_MET2.pdf}
-  \caption{We can use realizations of the IHMM to generate trajectories which 
+  \caption{We can use realizations of the HDP-AR-HMM to generate trajectories which 
   bear qualitative resemblance to the MD trajectories. We used the parameters 
-  of the IHMM, whose state segments are visualized in 
+  of the HDP-AR-HMM, whose state segments are visualized in 
   Figure~\ref{fig:rz_unclustered}, in order to construct an ensemble of 
   characteristic trajectories. Solute trajectories generated with
-  the IHMM (blue) show the same hopping and trapping behavior exhibited by 
+  the HDP-AR-HMM (blue) show the same hopping and trapping behavior exhibited by 
   MD (black).
@@
   MD MSDs on long timescales within uncertainty using realizations of the 
-  IHMM.
+  HDP-AR-HMM.
   \begin{itemize}
@@
     trajectories with uncharacteristically high MSDs. Despite our best efforts, 
-    we could not adequately parameterize an IHMM which reproduced said 
+    we could not adequately parameterize an HDP-AR-HMM which reproduced said 
     behavior. (see SI)  %BJC4: TODO
@@
   \caption{The MD MSDs (black) of methanol and urea are under-predicted by 
-  the IHMM (orange), while the predictions match within uncertainty for ethylene
+  the HDP-AR-HMM (orange), while the predictions match within uncertainty for ethylene
   glycol and acetic acid}\label{fig:unclustered_msds}
@@
 
-  \subsection{Using IHMM Parameters to Predict Selectivity}\label{section:macroscopic_properties}
+  \subsection{Using HDP-AR-HMM Parameters to Predict Selectivity}\label{section:macroscopic_properties}
 
@@
   \begin{itemize}
-    \item The IHMM MSD predictions quickly enter a linear regime, therefore we can 
+    \item The HDP-AR-HMM MSD predictions quickly enter a linear regime, therefore we can 
     project long timescale MSDs based on the predicted diffusion constant as described
@@
 
-  \subsection{Learning Mechanisms from the IHMM}\label{section:mechanisms}
+  \subsection{Learning Mechanisms from the HDP-AR-HMM}\label{section:mechanisms}
 
@@
   between monomer and solute chemical functionality. Our application of the 
-  IHMM can identify and distinguish these behaviors. The following approach 
+  HDP-AR-HMM can identify and distinguish these behaviors. The following approach 
   to analysis demonstrates how one can discover and explain the very complex
@@
   manageable size, and to allow different solute trajectories to share 
-  similar behavior, we clustered the states identified by the IHMM for each
+  similar behavior, we clustered the states identified by the HDP-AR-HMM for each
   solute as described in Section~\ref{method:clustering}. In 
@@
 
-  In addition to qualitative mismatches, realizations of the clustered IHMM 
+  In addition to qualitative mismatches, realizations of the clustered HDP-AR-HMM 
   under-predict the unclustered MSD predictions and the MD MSD. 
@@
 %    distributions generated directly from MD simulations to that generated from 
-%    realizations of the IHMM. 
+%    realizations of the HDP-AR-HMM. 
 %    \item We do this by measuring the time spent in each independent same-state segment.
 %    \item Some of the probability density of short trapping times in the MD simulations 
-%    gets shifted to medium length trapping times in realizations of the IHMM. 
+%    gets shifted to medium length trapping times in realizations of the HDP-AR-HMM. 
 %    \item In Figure~\ref{fig:dwell_distributions_modT} and~\ref{fig:msd_modT}, we show 
@@
 
-  We have shown that the IHMM can be used to automatically parameterize solute 
+  We have shown that the HDP-AR-HMM can be used to automatically parameterize solute 
   time series with an unknown number of latent dynamical modes. Initially, we applied
@@
   simulations. Vector autogregressive models can describe a diverse set of behavior
-  and so the IHMM may be suited to study many types motion, including those not 
-  characterized by hopping and trapping. The IHMM is a powerful approach for 
+  and so the HDP-AR-HMM may be suited to study many types motion, including those not 
+  characterized by hopping and trapping. The HDP-AR-HMM is a powerful approach for 
   understanding particle motion as well as for generating inexpensive models
@@
 % LocalWords:  nanostructure carboxylate VMD nonidealities hbonds outlier GAANN
-% LocalWords:  autogregressive PRF ACS XSEDE ACI IHMM nanoporous flowback evy
+% LocalWords:  autogregressive PRF ACS XSEDE ACI HDP-AR-HMM nanoporous flowback evy
 % LocalWords:  timescale subdiffusive coscia subdiffusion calderon GROMACS der

### 2020-05-16 Ben_Manuscripts/hdphmm/Draft.tex
Comments.

@@
   predicting bulk properties characteristic of much longer time scales. In this work 
-  we apply the sticky hierarchical Dirichlet process hidden Markov model (HDP-AR-HMM) 
+  we apply the sticky hierarchical Dirichlet process hidden Markov model (HPD-AR-HMM) 
+  %MRS: might be confusing to have the AR in there when the words ``Auto-regressive'' 
+  %don't appear; then they would try to figure out where the AR is. 
   to solute center-of-mass trajectories generated from long molecular dynamics 
@@
   solutes and the membrane. 
-
   Along with parameters of individual states, the HDP-AR-HMM simultaneously infers a transition
@@
 
+  %MRS: we have to decide if ``effective'' is the right word. Alternative is ``promising''.
   Overall, this work provides an effective way to simultaneously identify transport 
   mechanisms in nanoporous materials and project complex diffusive behavior on
-  long time scales.  This enhancement to our understanding of the diverse range 
+  long time scales.  
+  %MRS: simplify by removing nominalizations.
+  %This enhancement to our understanding 
+  Our enhanced understanding
+  of the diverse range 
   of solute behavior allows us to hypothesize design changes 
@@
   separations of the components of complex aqueous streams. Seawater and
-  bracksih water desalination, separation of organic micropollutants from 
+  brackish water desalination, separation of organic micropollutants from 
   municipal water supplies, recovering valuable dissolved species from 
@@
   selectivity in terms of detailed chemically dependent solute motion, then we can more
-  easily bridge the disconnect between theory and application. In many systems, it's 
+  easily bridge the disconnect between theory and application. In many systems, it is 
   possible to achieve this by calculating diffusion constants. 
@@
   % BJC4: seems like we should be addressing the problem as short time scale subdiffusive 
-  % dynamics that dictates measureable long time scale diffusion. Although curves become linear,
+  % dynamics that dictates measurable long time scale diffusion. Although curves become linear,
   % the slopes should be a product of the short time scale motion.
@@
   by the non-Brownian hopping and trapping behavior induced by the membrane's diverse
-  topology and inhomogeneous structure.~\cite{coscia_understanding_2019,coscia_chemically_2019}
-
-  We have already progressed our understanding of LLC monomer design in our previous work
+  topology and inhomogeneous structure result in subdiffusive behaviour out to multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
+  %MRS: to sentence above added to come back to main theme
+
+  We have already advanced our understanding of LLC monomer design in our previous work
   by building stochastic time series models based on the chemical intuition gained
@@
   membrane.~\cite{coscia_chemically_2019,coscia_capturing_2020} We identified three 
-  classes of trapping behavior which result in short time scale subdiffusion. In our 
+  classes of trapping behavior which result in 
+  %MRS: tweaked
+  subdiffusion out to the microsecond time scale. 
+  In our 
   first approach to stochastically model this behavior, we treated the system's dynamics
@@
   matched the behavior of solutes. It would be significantly more useful and broadly 
-  applicable if we could design an approach which automatically distinguishes and 
-  parameterizes varied solute dynamics and leaves a facile way to generate an ensemble
+  applicable if we could design an approach which 
+  %MRS: tweaked to sound more machine-learning-y
+  %automatically 
+  distinguishes and 
+  parameterizes varied solute dynamics 
+  in a data-driven way
+  and leaves a facile way to generate an ensemble
   of stochastic trajectory realizations that can be used to predict macroscopic transport
@@
   It also possible to achieve the same results using a Bayesian 
-  framework.~\cite{scott_bayesian_2002,jasra_markov_2005} One can place priors
+  framework.~\cite{scott_bayesian_2002,jasra_markov_2005} 
+  %MRS: not entirely clear what purpose of above sentence its - it sort of implied you will use Bayesian framework?
+  One can place priors
   on the transition probabilities and parameters of the hidden states' emission
   distributions in order to iteratively infer their values and to estimate the hidden state
-  sequence. HMMs have been used in a broad range of applications including speech
-  recognition, weather forecasting and bioinformatics.~\cite{juang_hidden_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}. In molecular simulations, HMMs have been
+  sequence. 
+  HMMs have been used in a broad range of applications including speech
+  recognition, weather forecasting and bioinformatics.~\cite{juang_hidden_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}.
+  In molecular simulations, HMMs have been
   used to characterize molecular kinetics in order to determine the equilibrium 
   distribution of various observables.~\cite{noe_probability_2008}
-
+  %MRS: probably a few more citations that should be added above, since there has been a lot.
   By placing a hierarchical Dirichlet process (HDP) prior on the transition 
@@
 
-  One issue with the original formulation of the HDP-HMM, is that it does 
+  One issue with the original formulation of the HDP-HMM is that it does 
   not distinguish self-transitions and transitions between different states.
@@
 
+  %MRS: define what ``this'' is - important claim, make it clear what it is you are claiming.
   To our knowledge, this is a novel application and analysis of the sticky 
@@
 
-  We ran all MD simulations and energy minimizations using GROMACS 2018.
-  ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}  
-  Our python implementation of the HDP-AR-HMM algorithm is available online at \\
+  We ran all MD simulations and energy minimizations using GROMACS 2018.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}  
+  Our Python implementation of the HDP-AR-HMM algorithm is available online at \\
+  %MRS: possibly should give the permanent reference to a shirtsgroup fork?  We can discuss which is likely to be more permenant
   \texttt{https://github.com/bencoscia/hdphmm}. All other post-simulation 
@@
   atomistic molecular model of four pores in a monoclinic unit cell with 
-  10 \% water by weight. Approximately one third of the water molecules 
-  occupy the tail region with the rest near the pore center.
+  10\% water by weight. Approximately one third of the water molecules 
+  occupy the tail region with the rest near the pore center.%MRS: cite previous paper here on this.
 
@@
 
-  We let each solute undergo 5 $\mu$s of MD simulation. We used a time step of 2 fs
+  %MRS: tweaked
+  %We let each solute undergo 
+  Each solute system was simulated for 5 $\mu$s of molecular dynamics  simulation. We used a time step of 2 fs
   at a pressure of 1 bar and temperature of 300K controlled by the Parrinello-Rahman 
+  %MRS: just wondering, was this semiisotropic, or isotropic?  If isotropic, do we know how different the diagonals of the 
+  pressure tensor were (since the system is not totally isotropic)
   barostat~\cite{parrinello_polymorphic_1981} and velocity rescale 
@@
 
+  %MRS: some of this is a repetition of what you said above.
   We implemented the sticky HDP-AR-HMM in Python 
@@
   covariance, $\Sigma$. We limited our analysis to an autoregressive order of $r=1$.
-  This means that we only parameterize $A_1$. To simplify notation, we will just
-  call it $A$. We used conjugate matrix-normal inverse-Wishart (MNIW) prior on parameters 
+  This means that we only parameterize $A_1$. To simplify notation, we will call it $A$. 
+  We used a conjugate matrix-normal inverse-Wishart (MNIW) prior on parameters 
   $A$ and $\Sigma$ and a Gaussian prior on $\mathbf{c}$ in order to infer their 
@@
   rather than the distance threshold. For our data, non-parametric methods such as 
-  Dirchlet process Gaussian mixture models~\cite{pedregosa_scikit-learn_2011,gelman_bayesian_2013}
+  Dirichlet process Gaussian mixture models~\cite{pedregosa_scikit-learn_2011,gelman_bayesian_2013}
   tend to delocalize the clusters in parameter space (see Section~\ref{S-section:agglomerative}
@@
   pore, transitioning from hydrophilic pores to hydrophobic tails. However, the 
-  channels are isotropic along the pore axis so we do not in means in the $z$ dimension.
+  channels are isotropic along the pore axis so we do not 
+  %MRS: added this?  Grammar didn't make sense without.
+  cluster
+  in means in the $z$ dimension.
   We normalized each clustering dimension by its variance and shifted the mean to zero.
@@
   $\lambda_y$ and $\lambda_x^2$ + $\lambda_y^2$ respectively, which are invariant with 
-  rotation around the $z$ axis, in both cases reducing the dimensionality from 3 to 2.  
+  rotation around the $z$ axis. 
+  %MRS: maybe reduntant and not quite right, since it reduces the dimensionality of the paraameter su
+  % bspace from 3 to 2, but the overall paameter space is bigger than 3
+  %in both cases reducing the dimensionality from 3 to 2.  
   We clustered on squared means in $r$, $\mu_r^2 = \mu_x^2 + \mu_y^2$, rather than
@@
   different kinds of trapping behavior related to hydrogen bonding and sodium ion association.
-
+  %MRS: last sentence is a little weird. Audience may be left without knowing how this could be achieved.
   %\subsubsection*{Choosing the Number of Clusters}
@@
   %BJC4: reworked this section
+  %MRS: should explain why here there are two approaches.
   \textit{Generating Stochastic HDP-AR-HMM Trajectory Realizations}: We used two 
@@
 
+  %MRS: this doesn't make sense - there aren't 1000 trajectories.  You mean method 1?
   For MD trajectories, we bootstrapped according to Method 2.
@@
   where $n$ is the number of spatial dimensions (1 in our case). Since the MSD
-  of our models enters a linear regime, we can estimate diffusion constants 
+  %MRS: tweaked
+  %of our models 
+  of the realizations of our models 
+  enters a linear regime, we can estimate diffusion constants 
+  %MRS: maybe can say what the timescale of the linear regime, and how much longer the stochastic realizations are?
   based on the slope of the linear region of the predicted MSD curves.
@@
   percentile of hydrogen bond lifetimes since their distribution is not Gaussian
-  and to emphasize longer trapping periods.~\cite{coscia_chemically_2019}
+  and to 
+  %MRS: 
+  %emphasize 
+  accentuate
+  longer trapping periods.~\cite{coscia_chemically_2019}
 
@@
   \caption{The HDP-AR-HMM found 24 distinct VAR(1) states in this representative methanol trajectory.
-  We performed the parameterization in 3D cartesian coordinates, but for this figure, we 
+  We performed the parameterization in 3D Cartesian coordinates, but for this figure, we 
   converted to cylindrical coordinates, with $r$ the distance from the pore center, to 
@@
     in their long term predictions.
-    \item We underestimate the MSD of Urea because of a small number of MD 
+    \item We underestimate the MSD of urea because of a small number of MD 
     trajectories with uncharacteristically high MSDs. Despite our best efforts, 
@@
   \caption{5 out of the 10 clustered states are visited by 15 or more of the solute
-  trajecotries. The solutes spend varying amounts of time in each of these states.
+  trajectories. The solutes spend varying amounts of time in each of these states.
   }
@@
     \item Therefore, it is logical to search for hydrogen bonding interactions
-    and solute assocation with sodium ions.
+    and solute association with sodium ions.
   \end{itemize}
@@
     \item In Figure~\ref{fig:hbond_fractions}, we show that methanol participates
-    in hydrogen bonds to various parts of the monomer between 27 and 45 \% of the
+    in hydrogen bonds to various parts of the monomer between 27 and 45\% of the
     total time it occupies the dominant states.
-    \item Methanol associates with sodium ions less than 10 \% of the time in 
+    \item Methanol associates with sodium ions less than 10\% of the time in 
     dominant states.
@@
   of hydrogen bond lifetimes. (d) We also analyzed the frequency and lifetimes of solute 
-  association with sodium ions. Methanol associates with sodium less than 10 \% of the total 
+  association with sodium ions. Methanol associates with sodium less than 10\% of the total 
   time it occupies any of the dominant state.
-  %Relative to hydrogen bonding, it is a relatively infrequenct interaction
+  %Relative to hydrogen bonding, it is a relatively infrequent interaction
   %for methanol molecules, but the 
@@
 % LocalWords:  scannable subsubcaptions errorbars uncharacteristicness facelift
-% LocalWords:  PSC RMACC hdphmm TOC
+% LocalWords:  PSC RMACC hdphmm TOC nominalizations dischinger ramaseshan Baum
+% LocalWords:  functionalized teuerle jasra markov bioinformatics hughes yoon
+% LocalWords:  hines diarization MJLSs MJLS SLDSs SLDS hamada jk params MNIW
+% LocalWords:  plateaued nclusters leftmargin trans diffusivity sorption alkane
+% LocalWords:  ness substituents

### 2020-05-17 Ben_Manuscripts/hdphmm/Draft.tex
update draft.

@@
   The number of states found for each trajectory varied between 5 and 30.  %BJC4: MET: (5, 28), need to finalized
-  In Figure~\ref{fig:rz_unclustered}, we show the state sequence determined by the HDP-AR-HMM for
+  Figure~\ref{fig:rz_unclustered}, shows the state sequence determined by the HDP-AR-HMM for
   an example methanol trajectory. The model distinguishes many of the states due to 
@@
   As shown in Figure~\ref{fig:qualitative_unclustered}, realizations of our model 
+  %MRS: would it be accurate to show ``produces trajectories that show . . . ``  Saying that it ``can 
+  %produce trajectories'' is a little weasly - sounds like it usually doesn't.  
+  % 
   can produce trajectories that show qualitatively similar hopping and trapping 
@@
   % BJC4: This figure needs to be redone with new trajectory generation procedure
+  %MRS: is this still the old one?
   \begin{figure}
@@
     Section~\ref{method:realizations} of the methods.
+    %MRS: should be clearer about what ``reproduce these curves mean'', since you aren't reproducing.
     \item Our ability to reproduce these curves gives use confidence
     in their long term predictions.
+    %MRS: not match under any circumstance, or without clustering (?  Not clear. 
     \item We underestimate the MSD of urea because of a small number of MD 
@@
   \subsection{Using HDP-AR-HMM Parameters to Predict Selectivity}\label{section:macroscopic_properties}
+
+  %MRS: seems odd not at least mention clustering here.
 
@@
   % BJC4: Not sure if this is useful.
-  By studying the parameters, it is now easier to describe the state behavior.
+  % MRS: it does give a good summary. But you should make it clear how you selected these 5.
+  % MRS: it's implied in one of the figures, but should be stated explicitly
+  By examining the parameters, it is now easier to describe the state behavior.
   \begin{enumerate}[label={State \theenumi :}, leftmargin=3.5\parindent]
@@
      The radial mean and evidence from Figure~\ref{fig:clustered_traj_MET} suggests
+     %MRS: ``tail and pore region'' sounds the same as ``everywhere''.
      that this state is common in the tail and pore region.
@@
      It is short lived and takes very large hops. This type of behavior is exhibited 
+     %MRS: ``near and far'' also sounds like everywhere 
      near and far from the pore center as discussed earlier.
@@
   \end{itemize}
-
+  %MRS: above, start with the last point; state what the interactions are, and then give the reasoning.
   For methanol, hydrogen bonding is a much more dominant interaction than sodium
@@
     simulation time.  
+    %MRS: this above doesn't support the thesis statement?
     \item Figure~\ref{fig:local_densities} helps to illustrate how the local density of 

### 2020-05-19 Ben_Manuscripts/hdphmm/Draft.tex
moving figures to SI

@@
   predicting bulk properties characteristic of much longer time scales. In this work 
-  we apply the sticky hierarchical Dirichlet process hidden Markov model (HPD-AR-HMM) 
-  %MRS: might be confusing to have the AR in there when the words ``Auto-regressive'' 
-  %don't appear; then they would try to figure out where the AR is. 
-  to solute center-of-mass trajectories generated from long molecular dynamics 
+  we apply the sticky hierarchical Dirichlet process autoregressive hidden Markov model
+  (HPD-AR-HMM) to solute center-of-mass trajectories generated from long molecular dynamics 
   simulations in a cross-linked inverted hexagonal phase lyotropic liquid crystal
@@
   %MRS: we have to decide if ``effective'' is the right word. Alternative is ``promising''.
-  Overall, this work provides an effective way to simultaneously identify transport 
+  %BJC5: ``promising'' seems safer
+  Overall, this work provides a promising way to simultaneously identify transport 
   mechanisms in nanoporous materials and project complex diffusive behavior on
-  long time scales.  
-  %MRS: simplify by removing nominalizations.
-  %This enhancement to our understanding 
-  Our enhanced understanding
-  of the diverse range 
-  of solute behavior allows us to hypothesize design changes 
-  to LLC monomers aimed towards controlling the rates of solute passage, thus improving 
-  the selective performance of LLC membranes.
+  long time scales. Our enhanced understanding of the diverse range of solute behavior
+  allows us to hypothesize design changes to LLC monomers aimed towards controlling the
+  rates of solute passage, thus improving the selective performance of LLC membranes.
 
@@
   by the non-Brownian hopping and trapping behavior induced by the membrane's diverse
-  topology and inhomogeneous structure result in subdiffusive behaviour out to multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
-  %MRS: to sentence above added to come back to main theme
+  topology and inhomogeneous structure resulting in subdiffusive behavior out to 
+  multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
 
@@
   membrane.~\cite{coscia_chemically_2019,coscia_capturing_2020} We identified three 
-  classes of trapping behavior which result in 
-  %MRS: tweaked
-  subdiffusion out to the microsecond time scale. 
-  In our 
-  first approach to stochastically model this behavior, we treated the system's dynamics
-  as a sequence of anti-correlated hops between power law distributed periods of 
+  classes of trapping behavior which result in subdiffusion out to the microsecond 
+  time scale. In our first approach to stochastically model this behavior, we treated 
+  the system's dynamics as a sequence of anti-correlated hops between power law distributed periods of 
   entrapment, a framework called subordinated fractional Brownian or L\'evy
@@
   matched the behavior of solutes. It would be significantly more useful and broadly 
-  applicable if we could design an approach which 
-  %MRS: tweaked to sound more machine-learning-y
-  %automatically 
-  distinguishes and 
-  parameterizes varied solute dynamics 
-  in a data-driven way
-  and leaves a facile way to generate an ensemble
+  applicable if we could design an approach which distinguishes and parameterizes varied
+  solute dynamics in a data-driven way and leaves a facile way to generate an ensemble
   of stochastic trajectory realizations that can be used to predict macroscopic transport
@@
   Given a series of observations and a known number of hidden states, the 
-  Baum-Welch algorithm is the most commonly used way to determine the hidden
-  state sequence and the underlying parameters of a standard HMM.~\cite{baum_maximization_1970}
-  It also possible to achieve the same results using a Bayesian 
-  framework.~\cite{scott_bayesian_2002,jasra_markov_2005} 
+  Baum-Welch algorithm, an expectation maximization technique, is the most commonly 
+  used way to determine the hidden state sequence and the underlying parameters of
+  a standard HMM.~\cite{baum_maximization_1970} It also possible to achieve the same
+  results using a Bayesian framework.~\cite{scott_bayesian_2002,jasra_markov_2005} 
   %MRS: not entirely clear what purpose of above sentence its - it sort of implied you will use Bayesian framework?
-  One can place priors
-  on the transition probabilities and parameters of the hidden states' emission
-  distributions in order to iteratively infer their values and to estimate the hidden state
-  sequence. 
-  HMMs have been used in a broad range of applications including speech
-  recognition, weather forecasting and bioinformatics.~\cite{juang_hidden_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}.
-  In molecular simulations, HMMs have been
-  used to characterize molecular kinetics in order to determine the equilibrium 
-  distribution of various observables.~\cite{noe_probability_2008}
-  %MRS: probably a few more citations that should be added above, since there has been a lot.
+  % BJC5: Baum welch is most widely used for pure HMM but is an expectation maximization algorithm
+  % There are pure Bayesian ways to do it. Tried to clarify above.
+  One can place priors on the transition probabilities and parameters of the hidden 
+  states' emission distributions in order to iteratively infer their values and to
+  estimate the hidden state sequence. HMMs have been used in a broad range of applications
+  including speech recognition, weather forecasting and bioinformatics.~\cite{juang_hidden_1984,hughes_non-homogeneous_1999,yoon_hidden_2009}.
+  In molecular simulations, HMMs have been used to characterize molecular kinetics
+  in order to determine the equilibrium distribution of various observables.~\cite{thayer_hidden_2002,singhal_using_2004,noe_probability_2008,noe_projected_2013}
+
   By placing a hierarchical Dirichlet process (HDP) prior on the transition 
@@
   %MRS: define what ``this'' is - important claim, make it clear what it is you are claiming.
-  To our knowledge, this is a novel application and analysis of the sticky 
-  HDP-AR-HMM. Typical applications center around determining the number of
-  states, the state sequence and occasional analysis of the emission 
-  distributions. The addition of temporal correlation to the inference 
-  procedure has primarily been used to improve state sequence 
+  To our knowledge, applying the HDP-AR-HMM in order to gain kinetic and
+  mechanistic insight from MD simulation trajectories has not been done
+  before.
+  % this is a novel application and analysis of the sticky HDP-AR-HMM.
+  Typical applications of the HDP-AR-HMM center around determining the 
+  number of states, the state sequence and occasional analysis of the emission 
+  distributions of a time series. The addition of temporal correlation to 
+  the inference procedure has primarily been used to improve state sequence 
   identification.~\cite{calderon_inferring_2015,hamada_modeling_2016}
@@
   solute kinetics. Further, we use the model parameters to generate new 
-  time series trajectories which enable projections of MD simulations on 
+  time series trajectories which enables projections of MD simulations on 
   much longer time scales.
@@
   We ran all MD simulations and energy minimizations using GROMACS 2018.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}  
-  Our Python implementation of the HDP-AR-HMM algorithm is available online at \\
+  We implemented the sticky HDP-AR-HMM in Python 
+  (\texttt{https://github.com/bencoscia/hdphmm}) which we heavily adapted from
+  the MATLAB code of Fox et al.~\cite{fox_nonparametric_2009} Since we do not incorporate
+  any novel methodology to the HDP-AR-HMM inference procedure, we refer the 
+  interested reader to an excellent and in-depth description of the formulation of
+  the HDP-AR-HMM and related models.~\cite{fox_bayesian_2010} 
   %MRS: possibly should give the permanent reference to a shirtsgroup fork?  We can discuss which is likely to be more permenant  
-  \texttt{https://github.com/bencoscia/hdphmm}. All other post-simulation 
-  trajectory analysis tools are available online at
+  All other post-simulation trajectory analysis tools are available online at
   \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
@@
 
-  %MRS: tweaked
-  %We let each solute undergo 
-  Each solute system was simulated for 5 $\mu$s of molecular dynamics  simulation. We used a time step of 2 fs
-  at a pressure of 1 bar and temperature of 300K controlled by the Parrinello-Rahman 
-  %MRS: just wondering, was this semiisotropic, or isotropic?  If isotropic, do we know how different the diagonals of the 
-  pressure tensor were (since the system is not totally isotropic)
+  Each solute system was simulated for 5 $\mu$s of molecular dynamics simulation. We
+  used a time step of 2 fs at a pressure of 1 bar and temperature of 300K controlled
+  by the semi-isotropic Parrinello-Rahman 
+  %MRS: just wondering, was this semiisotropic, or isotropic?  If isotropic, do we know how different the diagonals of the pressure tensor were (since the system is not totally isotropic)
+  %BJC5: I use semi-isotropic (xy together and z separate)
   barostat~\cite{parrinello_polymorphic_1981} and velocity rescale 
@@
   \subsection{Applying the sticky HDP-AR-HMM to MD Trajectories}\label{method:HDP-AR-HMM}
-
-  % BJC4: Chris' general comment for this section: 'the problem with this section is 
-  % that it doesn't help the expert or novice figure out what is being done (either 
-  % expand more or relegate details to references and talk bigger picture)'
-
-  % BJC4: I think it makes sense to stick to bigger picture since there are much
-  % better descriptions in literature. I haven't made any modifications to what's already been done
-
-  % BJC4: replaced with what follows. Lots of the big picture is in the intro
-
-%  \subsubsection*{Extending Hidden Markov Modeling to an Unknown Number of States}
-%  
-%  Hidden Markov models (HMMs) are a useful and widely used technique for modeling
-%  sequences of observations where the probability of the next observation in a 
-%  sequence depends, at least in part, on a previous unobserved, latent or hidden,
-%  state.~\cite{beal_infinite_2002} In the context of our simulations, the observations
-%  correspond to the center of mass coordinates of the solutes versus time, and the
-%  states correspond to segments of the trajectory with similar dynamical behavior 
-%  which gives rise to those types of observations. The probability of transitioning 
-%  to a state based on the current state is defined in terms of an $n\times n$ 
-%  transition probability matrix, $T$, where $n$ is the number of states. Unfortunately,
-%  standard HMMs require $n$ to be known \textit{a priori}. One can partially overcome
-%  this by testing a range of numbers of hidden states and determining which is the
-%  best representation of the data.~\cite{pohle_selecting_2017}
-%  
-%  The infinite-state HMM overcomes this drawback by placing a hierarchical
-%  Dirichlet process (HDP) prior on the transition probabilities.~\cite{fox_bayesian_2010} Using some 
-%  base probability distribution, $H$, a Dirichlet process (DP) generates discrete 
-%  distributions, $G_0$, over a countably infinite number of probability measures:
-%  \begin{equation}
-%      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
-%  \end{equation}
-%  where the $\theta_k$ are values drawn from the base distribution and the weights
-%  $\beta_k$ come from a stick-breaking process parameterized by the concentration 
-%  parameter $\gamma$ (equivalently referred to as GEM($\gamma$)).~\cite{halmos_random_1944} In shorthand, this
-%  specification can be expressed as $G_0 \sim DP(\gamma, H)$. The concentration 
-%  parameter, $\gamma$, expresses one's confidence in the base distribution $H$.
-%  We use a uniform base distribution for $H$. When $\gamma\to 0$, the first 
-%  weight of $G_0$, $\beta_1$, approaches unity and for $\gamma\to\infty$, the weights
-%  become uniform and $G_0$ closely resembles $H$. Each row, $G_j$, of the transition 
-%  matrix is produced by drawing from a DP specified using the $\beta$ vector as a 
-%  discrete base distribution and a separate concentration parameter, $\alpha$.
-%  \begin{equation}
-%      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
-%  \end{equation}
-%  This hierarchical specification ensures that the transition probabilities in 
-%  each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
-%  Once the model has converged only a finite number of states will have significant
-%  sampling.
 
@@
   in order to emphasize self-transitions since we expect solutes to stay trapped in
-  states for appreciable amounts of time. We analyze solute motion in terms of their
-  cylindrical coordinates, $(r, z)$, with the $z$ axis oriented along the membrane 
-  pores and the radial dimension, $r$, measured from the closest pore center.
+  states for appreciable amounts of time. 
+%  We analyze solute motion in terms of their
+%  cylindrical coordinates, $(r, z)$, with the $z$ axis oriented along the membrane 
+%  pores and the radial dimension, $r$, measured from the closest pore center.
 
@@
   with the radial dimension represented by the solute's $x$ and $y$ coordinates 
-  transformed relative to the nearest pore center. By working in Cartesian coordinates,
-  we avoid mathematical complexity introduced by change of coordinates into cylindrical
-  coordinates while estimating the state sequence.
-
-  %MRS: some of this is a repetition of what you said above.
-  We implemented the sticky HDP-AR-HMM in Python 
-  (\texttt{https://github.com/bencoscia/hdphmm}) which we heavily adapted from
-  the MATLAB code of Fox et al.~\cite{fox_nonparametric_2009} Since we do not incorporate
-  any novel methodology to the HDP-AR-HMM inference procedure, we refer the 
-  interested reader to an excellent and in-depth description of the formulation of
-  the HDP-AR-HMM and related models.~\cite{fox_bayesian_2010}
+  transformed relative to the nearest pore center, and the $z$ axis oriented along 
+  the membrane pore. By working in Cartesian coordinates, we avoid mathematical 
+  complexity introduced by change of coordinates into cylindrical coordinates while
+  estimating the state sequence.
 
@@
   pore, transitioning from hydrophilic pores to hydrophobic tails. However, the 
-  channels are isotropic along the pore axis so we do not 
-  %MRS: added this?  Grammar didn't make sense without.
-  cluster
-  in means in the $z$ dimension.
-  We normalized each clustering dimension by its variance and shifted the mean to zero.
+  channels are isotropic along the pore axis so we do not cluster in means in the 
+  $z$ dimension. We normalized each clustering dimension by its variance and shifted
+  the mean to zero.
 
@@
   $\lambda_y$ and $\lambda_x^2$ + $\lambda_y^2$ respectively, which are invariant with 
-  rotation around the $z$ axis. 
-  %MRS: maybe reduntant and not quite right, since it reduces the dimensionality of the paraameter su
-  % bspace from 3 to 2, but the overall paameter space is bigger than 3
-  %in both cases reducing the dimensionality from 3 to 2.  
-  We clustered on squared means in $r$, $\mu_r^2 = \mu_x^2 + \mu_y^2$, rather than
-  $\mu_x$ and $\mu_y$ individually, with the square $\mu_r$ converting it into the 
-  same units as $A$ and $\Sigma$.
+  rotation around the $z$ axis. We clustered on squared means in $r$, 
+  $\mu_r^2 = \mu_x^2 + \mu_y^2$, rather than $\mu_x$ and $\mu_y$ individually, with the
+  square $\mu_r$ converting it into the same units as $A$ and $\Sigma$.
 
@@
   value of the number of sequential self-transitions is simply:
-  % BJC4: I numbered this equation because I reference it later.
   \begin{equation}  
@@
 
-  %BJC4: Added
   There are alternative ways to cluster the data dependent on one's goals. Our goal is
@@
   beneficial to incorporate other physically motivated variables into the clustering
-  procedure. For example, one can gain a thorough understanding of the dynamics of
-  different kinds of trapping behavior related to hydrogen bonding and sodium ion association.
+  procedure. 
+  %For example, one can gain a thorough understanding of the dynamics of
+  %different kinds of trapping behavior related to hydrogen bonding and sodium ion association.
   %MRS: last sentence is a little weird. Audience may be left without knowing how this could be achieved.
-  %\subsubsection*{Choosing the Number of Clusters}
 
@@
 
-%  We aimed to maintain the highest silhouette score, and thus lowest number of clusters,
-%  possible while preserving the dynamics of each trajectory.
-%  %verifying that visually distinct states stayed separated. 
-%  We verified preservation of the dynamics by comparing the MSDs of stochastic trajectory
-%  realizations based on clustered HDP-AR-HMM parameter sets to the pooled MSDs of stochastic 
-%  realizations of HDP-AR-HMMs fit to individual trajectories (see Section~\ref{method:realizations}).
-%%  We chose the lowest number of clusters that reasonably reproduced the pooled MSDs at 
-%%  short and long time lags (See Figure~\ref{S-fig:MET_nclusters} of the Supporting 
-%%  Information).
-
-  %\subsubsection*{Obtaining Parameters of Clustered States}
-
-  %BJC3: modified 
   \textit{Obtaining Parameters of Clustered States}: We remapped and fixed the
@@
   \textit{Generating Stochastic HDP-AR-HMM Trajectory Realizations}: We used two 
-  different methods to stochastically generate trajectories:
+  different methods to stochastically generate trajectories because generating
+  trajectories from clustered parameter sets can give results that are qualitatively 
+  and quantitatively different from those generated by unclustered parameter sets.
+  In our discussion we evaluate both methods:
   \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
@@
 
-  %MRS: this doesn't make sense - there aren't 1000 trajectories.  You mean method 1?
-  For MD trajectories, we bootstrapped according to Method 2.
+  For the MD MSDs, we bootstrapped according to Method 1, sampling with 
+  replacement from the ensemble of 24 solute trajectories.
 
@@
   where $n$ is the number of spatial dimensions (1 in our case). Since the MSD
-  %MRS: tweaked
-  %of our models 
-  of the realizations of our models 
-  enters a linear regime, we can estimate diffusion constants 
-  %MRS: maybe can say what the timescale of the linear regime, and how much longer the stochastic realizations are?
+  of the realizations of our models enters a linear regime, we can estimate 
+  diffusion constants 
+  % MRS: maybe can say what the timescale of the linear regime, and how much 
+  % longer the stochastic realizations are?
   based on the slope of the linear region of the predicted MSD curves.
@@
   percentile of hydrogen bond lifetimes since their distribution is not Gaussian
-  and to 
-  %MRS: 
-  %emphasize 
-  accentuate
-  longer trapping periods.~\cite{coscia_chemically_2019}
+  and to accentuate longer trapping periods.~\cite{coscia_chemically_2019}
 
@@
 
-  %We developed a way to 
   \textit{Local density measurements}: We measured the local density of the membrane at
@@
   As shown in Figure~\ref{fig:qualitative_unclustered}, realizations of our model 
-  %MRS: would it be accurate to show ``produces trajectories that show . . . ``  Saying that it ``can 
-  %produce trajectories'' is a little weasly - sounds like it usually doesn't.  
-  % 
-  can produce trajectories that show qualitatively similar hopping and trapping 
+  produce trajectories that show qualitatively similar hopping and trapping 
   behavior to the MD trajectories to which they were fit. It is important that our
@@
 
-  % BJC4: This figure needs to be redone with new trajectory generation procedure
-  %MRS: is this still the old one?
   \begin{figure}
@@
 
-  In Figure~\ref{fig:unclustered_msds}, we show that in most cases we can reproduce the 
-  MD MSDs on long timescales within uncertainty using realizations of the 
-  HDP-AR-HMM.
-  \begin{itemize}
-    \item We generated the MSD curves using Method 1 described in 
-    Section~\ref{method:realizations} of the methods.
-    %MRS: should be clearer about what ``reproduce these curves mean'', since you aren't reproducing.
-    \item Our ability to reproduce these curves gives use confidence
-    in their long term predictions.
+  In Figure~\ref{fig:unclustered_msds}, we show that in most cases we can 
+  reproduce the magnitude of the MD MSDs on long timescales within uncertainty
+  using realizations of the HDP-AR-HMM. We generated the MSD curves using Method
+  1 described in Section~\ref{method:realizations} of the methods. Our ability
+  to reproduce the MSDs gives us confidence in their long term predictions.
   %MRS: not match under any circumstance, or without clustering (?  Not clear. 
-    \item We underestimate the MSD of urea because of a small number of MD 
-    trajectories with uncharacteristically high MSDs. Despite our best efforts, 
-    we could not adequately parameterize an HDP-AR-HMM which reproduced said 
+  %BJC5: not exactly sure what you're asking here. This section has no clustering 
+  We underestimate the MSD of urea because of a small number of MD trajectories
+  with uncharacteristically high MSDs. Despite our best efforts, we could not 
+  adequately parameterize an HDP-AR-HMM which reproduced the uncharacteristic
   behavior. (see SI)  %BJC4: TODO
-    \item On long timescales, the model appear to have the same slope as 
-    the MD trajectory.
-  \end{itemize}
+  On long timescales, the model appear to have the same slope as the MD 
+  trajectory.
 
@@
   Since we can generate trajectories that share features similar to MD simulations, 
-  it is now reasonable to project solute behavior onto much longer time scales.
-  \begin{itemize}
-    \item The HDP-AR-HMM MSD predictions quickly enter a linear regime, therefore we can 
-    project long timescale MSDs based on the predicted diffusion constant as described
-    in Section~\ref{method:selectivity}.
-  \end{itemize}
+  it is now reasonable to project solute behavior onto much longer time scales. The 
+  HDP-AR-HMM MSD predictions quickly enter a linear regime, therefore we can project
+  long timescale MSDs based on the predicted diffusion constant as described in 
+  Section~\ref{method:selectivity}.
 
@@
 
-  % BJC4: some kind of brief selectivity analysis here. This easy, I'll get that done 
-  % tonight or tomorrow.
+  % BJC4: some kind of brief selectivity analysis here.
 
@@
   Realizations based on the 10 clustered parameter sets do not show the same
-  qualitative dynamics as the MD simulation trajectories. 
-  \begin{itemize}  
-    \item In Figure~\ref{fig:qualitative_clustered_MET}, we compare MD 
-    trajectories to realizations of our model using the clustered parameter sets.
-    \item They lack the diversity of behavior which we see in the MD simulation trajectories.
-    \item They do not show the same range of trapping times and hop lengths.
-    \item If we use a higher number of clusters, the qualitative match improves, but
-    at the cost of a larger state space to interpret (see Figure~\ref{S-fig:qualitative_improvement}
+  qualitative dynamics as the MD simulation trajectories. In 
+  Figure~\ref{fig:qualitative_clustered_MET}, we compare MD trajectories to 
+  realizations of our model using the clustered parameter sets. They lack the
+  diversity of behavior which we see in the MD simulation trajectories.
+  They do not show the same range of trapping times and hop lengths. If we use
+  a higher number of clusters, the qualitative match improves, but at the cost
+  of a larger state space to interpret (see Figure~\ref{S-fig:qualitative_improvement}
   of the Supporting Information).
-  \end{itemize}
 
   In addition to qualitative mismatches, realizations of the clustered HDP-AR-HMM 
-  under-predict the unclustered MSD predictions and the MD MSD. 
-  \begin{itemize}
-    \item Much of a solute's MSD is likely a consequence of short-lived trapping states
-    with high variances.
-    \item When clustering, disjoint segments with similar enough parameters are
-    re-parameterized together as part of the same state, lengthening the lifetimes 
-    of very short-lived states and suppressing the fluctuations of high variance states.
-    \item In Figure~\ref{fig:clustered_MSD}, it is evident that increasing the number
-    of clusters increases the predicted MSD.
-    \item Matching the unclustered MSDs would likely require many more clusters, at 
-    which point the benefits of clustering are lost. 
+  under-predict the unclustered MSD predictions and the MD MSD. Much of a solute's 
+  MSD is likely a consequence of short-lived trapping states with high variances.
+  When clustering, disjoint segments with similar enough parameters are re-parameterized
+  together as part of the same state, lengthening the lifetimes of very short-lived 
+  states and suppressing the fluctuations of high variance states. In 
+  Figure~\ref{fig:clustered_MSD}, it is evident that increasing the number of clusters
+  increases the predicted MSD. Matching the unclustered MSDs would likely require many
+  more clusters, at which point the benefits of clustering are lost. 
     %BJC: I don't think the following discussion is necessary anymore.
@@
 %    trapped states.
-  \end{itemize}
 
@@
 
+  %BJC5: new
+  It is possible that we could improve the MSD predictions generated by the 
+  clustered parameter sets by modifying the transformations made to the
+  unclustered parameters. For example, it maybe possible to rescale the
+  parameters in order to better distinguish states with long dwell times
+  and high variance when clustering.
+%  Since we hypothesized that the lack of short dwell
+%  times is largely responsible for the under-prediction of the MSDs, we could
+%  modify the dwell time clustering procedure in order to better emphasize short
+%  dwells times.
+  However, we do not go too far in order to prevent over-fitting.
+  %BJC5: maybe an SI figure showing some different approaches
+
   \textit{The dynamics of frequently occurring states}: We may learn the most by 
   studying the dynamical modes common to the majority of the solute trajectories.
-  \begin{itemize}
-  	\item Of the 10 state clusters, only 5 appear in a significant number of 
-  	solute trajectories (Figure~\ref{fig:prevalence}).
-  	\item Although a majority of the solutes visit these 5 dominant states the
-  	amount of time spent in each varies widely. 
-  \end{itemize}
+  Of the 10 state clusters, only 5 appear in a significant number of solute 
+  trajectories (Figure~\ref{fig:prevalence}). All of which are present in 
+  Figure~\ref{fig:clustered_traj_MET}. Although a majority of the solutes
+  visit these 5 dominant states the amount of time spent in each varies widely.
 
@@
 
-  We can begin to hypothesize mechanisms by studying the behaviors defined by the 
-  state parameters.
-  \begin{itemize}
-  	\item In Figure~\ref{fig:common_states_lines}, we plot representative 
-  	dynamics of each of the five most visited states.
-  	\item The states exhibit a range of autoregressive and trapping behavior
-  	throughout the membrane pores.
-%  	\item There is good representation by states across a range of radial distances
-%  	from the pore centers. 
-  \end{itemize}
-
-  Since the radial means are weighted averages of the states used to parameterize
-  each cluster, for interpretive purposes, it is important to recognize that the means
-  only provide clues towards the general location of the solute. 
-  \begin{itemize}
-  	\item For example, the radial mean of state 3 is 1.4 nm from the pore center. 
-  	\item However, inspection of Figure~\ref{fig:clustered_traj_MET} suggests that this 
-  	type of behavior actually occurs radially throughout the pore.
-  	\item There are instances of state 3 less than 1 nm from the pore center and more 
-  	than 2 nm from the pore center. 
-  	\item In this case, the radial mean only suggests that this type of behavior 
-  	happens in both regions somewhat equally.
-  \end{itemize}
-
-  Solutes exhibit a range of autoregressive behavior as shown by the representative 
-  solute trajectories in Figure~\ref{fig:common_states_lines} and the scatter
-  plot in Figure~\ref{fig:A_sigma_scatter}.
-  \begin{itemize}
-  	\item In most cases, the eigenvalues of $A$ and $\Sigma$ appear nearly paired
-  	in their radial and axial dimensions, which implies nearly symmetric behavior 
-  	with off-diagonals both matrices near zero.
-  	\item The most notable exception is state 3, which has a much higher radial 
-  	eigenvalue of the covariance matrix.
-  	\item Both eigenvalues of state 3's covariance are actually quite
-  	large. This implies relatively large fluctuations in the $z$ direction and even
-  	bigger fluctuations in the $r$ direction.
-  	\item All states have slightly lower covariance in the axial direction. It's
-  	likely easier for solutes to move laterally rather than to move up through the
-  	alkane chains.
-  	\item States 3 and 4 show a strong previous-hop dependence (high $A$) while
-  	the rest of the states have a somewhat weaker dependence.
-  \end{itemize}
-
-  Solutes are trapped for various lengths of time.
-  \begin{itemize}
-    \item On average, state 4 has the longest dwell times and state 3 has
-    the shortest dwell times while the rest have intermediate dwell times.
-    \item This is somewhat supported by inspection of Figure~\ref{fig:clustered_traj_MET},
-    however. 
-	\item The expected dwell times of the clusters incorporate all 24 trajectories.
-%    \item Once again, since we clustered, it is important to avoid studying
-%    the exact dwell time values, and to focus on their relative magnitudes.
-  \end{itemize}
-
-  % BJC4: Not sure if this is useful.
-  % MRS: it does give a good summary. But you should make it clear how you selected these 5.
-  % MRS: it's implied in one of the figures, but should be stated explicitly
-  By examining the parameters, it is now easier to describe the state behavior.
+  The parameters of the five dominant states provide clues about the associated solute
+  behavior. Characteristic dynamics of the following states appear in 
+  Figure~\ref{fig:clustered_traj_MET}. A more in-depth analysis of the state parameters
+  is given in Section~\ref{S-section:clustered_parmeters} of the Supporting Information.
   \begin{enumerate}[label={State \theenumi :}, leftmargin=3.5\parindent]
-     \item This state has intermediate dwell times with high past-hop dependence.
+     \item This state has intermediate dwell times with high past-hop dependence (high entries of $A$).
      The radial mean and evidence from Figure~\ref{fig:clustered_traj_MET} suggests
@@
   \end{enumerate}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.58\textwidth}
-  \includegraphics[width=\textwidth]{common_states.pdf}
-  \caption{}\label{fig:common_states_lines}
-  \end{subfigure}
-  \begin{subfigure}{0.41\textwidth}
-  \includegraphics[width=\textwidth]{A_sigma_scatter.pdf}
-  \caption{}\label{fig:A_sigma_scatter}
-  \includegraphics[width=\textwidth]{dwell_times.pdf}
-  \caption{}\label{fig:dwell_times}
-  \end{subfigure}
-  \caption{The 5 most visited states by methanol show a range of dynamical behavior. In 
-  (a), we show representative dynamics of these states. All time series have a mean of zero and are
-  shifted to put the mean in line with the $y$-axis labels for the purpose of visualizing them.
-  The $y$-axis labels of the $r$ coordinate plot specify the radial mean of each clustered 
-  state. All of the states pictured appear in the trajectory shown in 
-  Figure~\ref{fig:clustered_traj_MET} and are colored to match.
-  (b) We can begin to understand the solute behaviors demonstrated in (a) by understanding their VAR 
-  parameters. Higher values of $\lambda_{\Sigma}$ generally are indicative of large fluctuations
-  and higher values of $\lambda_A$ indicate strong previous-hop dependence of the fluctuations.
-  (c) Using Equation~\ref{eqn:dwell_times}, we estimated the expected time spent within each 
-  of the states.
-  }\label{fig:common_states_MET}
-  \end{figure}
 

### 2020-05-19 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Improvements to methods
moving figures to SI

@@
 
+  \section{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
+
+  The IHMM is quite powerful on its own, but requires some critical thinking by
+  the user in order to ensure maximum effectiveness. One can obtain 
+  the best results with some simple checks and, where necessary, improved 
+  state sequence initialization.
+
+  The best way to ensure reliable MSD predictions is to ensure proper reproduction
+  of the individual MD MSDs by realizations of the IHMM. Over-predictions and 
+  under-predictions are usually the result of a poorly identified state sequence. (see
+  Figure TBD for example)
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.35\textwidth}
+  \includegraphics[width=\textwidth]{overestimate_ACH_21.pdf}
+  \caption{}\label{fig:msd_overestimate}
+  \end{subfigure}
+  \begin{subfigure}{0.63\textwidth}
+  \includegraphics[width=\textwidth]{state_sequence_before_ACH_21.pdf}
+  \caption{}\label{fig:state_sequence_before}
+  \end{subfigure}
+  \begin{subfigure}{0.35\textwidth}
+  \includegraphics[width=\textwidth]{msd_improvement_ACH_21.pdf}
+  \caption{}\label{fig:msd_improvement}
+  \end{subfigure}
+  \begin{subfigure}{0.63\textwidth}
+  \includegraphics[width=\textwidth]{state_sequence_after_ACH_21.pdf}
+  \caption{}\label{fig:state_sequence_after}
+  \end{subfigure}
+  \caption{(a, b) In some cases, the state segmentation leads to over- or 
+  under-prediction of the MSD, usually due to poor initialization of the state
+  sequence. In (b), state transitions are too frequent and lead to an
+  overprediction of the MD MSD. (c) We can greatly improve MSD predictions by
+  giving the IHMM a good guess at the initial state sequence. (d) A better
+  initial state segmentation via seeding, gives more reasonable estimates
+  of the final state sequence.}\label{fig:improvement_state_sequence}
+  \end{figure}
+
+  There are two primary approaches we have implemented in order to improve the final 
+  state sequence predictions. Both attempt to aid the initial state assignments 
+  algorithmically. First, we always initialize the prior on $\mathbf{c}$ in 
+  Equation~\ref{M-eqn:var} of the main text as described in 
+  Section~\ref{section:prior_guesses}. In particularly tricky cases, the initial
+  state sequence estimate is so poor that qualitative trajectory realizations
+  and MSD predictions are irreconcilable with MD. In our second approach, we can
+  seed the initial state sequence with a guess made by applying the IHMM to 
+  smaller segments of the trajectory.
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_segment0.pdf}
+  \caption{Found 4 Unique States}\label{fig:segment1}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_segment1.pdf}
+  \caption{Found 14 Unique States}\label{fig:segment2}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_segment2.pdf}
+  \caption{Found 13 Unique States}\label{fig:segment3}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_segment3.pdf}
+  \caption{Found 12 Unique States}\label{fig:segment4}
+  \end{subfigure}
+  \begin{subfigure}{1\textwidth}
+  \includegraphics[width=\textwidth]{seed_ACH21_full.pdf}
+  \caption{Initial state sequence seeded with states found in (a)--(d)}\label{fig:full}
+  \end{subfigure}
+  \caption{In (a--d), we show the state sequence resulting from 5 iterations
+  of the IHMM on each of the four quarters of the center-of-mass trajectory in
+  (e) after splitting it into 4 separate segments. We use the concatenation 
+  of the four state sequences as the initial sequence for the IHMM run on the 
+  fully trajectory in (e).
+  }\label{fig:seed_sequence}
+  \end{figure}
+
 %  \subsection{Clustering on the self-transition probabilities}\label{section:selfT_cluster}
@@
 
-  \section{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
-
-  The IHMM is quite powerful on its own, but requires some critical thinking by
-  the user in order to ensure maximum effectiveness. One can obtain 
-  the best results with some simple checks and, where necessary, improved 
-  state sequence initialization.
-
-  The best way to ensure reliable MSD predictions is to ensure proper reproduction
-  of the individual MD MSDs by realizations of the IHMM. Over-predictions and 
-  under-predictions are usually the result of a poorly identified state sequence. (see
-  Figure TBD for example)
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.35\textwidth}
-  \includegraphics[width=\textwidth]{overestimate_ACH_21.pdf}
-  \caption{}\label{fig:msd_overestimate}
-  \end{subfigure}
-  \begin{subfigure}{0.63\textwidth}
-  \includegraphics[width=\textwidth]{state_sequence_before_ACH_21.pdf}
-  \caption{}\label{fig:state_sequence_before}
-  \end{subfigure}
-  \begin{subfigure}{0.35\textwidth}
-  \includegraphics[width=\textwidth]{msd_improvement_ACH_21.pdf}
-  \caption{}\label{fig:msd_improvement}
-  \end{subfigure}
-  \begin{subfigure}{0.63\textwidth}
-  \includegraphics[width=\textwidth]{state_sequence_after_ACH_21.pdf}
-  \caption{}\label{fig:state_sequence_after}
-  \end{subfigure}
-  \caption{(a, b) In some cases, the state segmentation leads to over- or 
-  under-prediction of the MSD, usually due to poor initialization of the state
-  sequence. In (b), state transitions are too frequent and lead to an
-  overprediction of the MD MSD. (c) We can greatly improve MSD predictions by
-  giving the IHMM a good guess at the initial state sequence. (d) A better
-  initial state segmentation via seeding, gives more reasonable estimates
-  of the final state sequence.}\label{fig:improvement_state_sequence}
-  \end{figure}
-
-  There are two primary approaches we have implemented in order to improve the final 
-  state sequence predictions. Both attempt to aid the initial state assignments 
-  algorithmically. First, we always initialize the prior on $\mathbf{c}$ in 
-  Equation~\ref{M-eqn:var} of the main text as described in 
-  Section~\ref{section:prior_guesses}. In particularly tricky cases, the initial
-  state sequence estimate is so poor that qualitative trajectory realizations
-  and MSD predictions are irreconcilable with MD. In our second approach, we can
-  seed the initial state sequence with a guess made by applying the IHMM to 
-  smaller segments of the trajectory.
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\textwidth]{seed_ACH21_segment0.pdf}
-  \caption{Found 4 Unique States}\label{fig:segment1}
-  \end{subfigure}
-  \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\textwidth]{seed_ACH21_segment1.pdf}
-  \caption{Found 14 Unique States}\label{fig:segment2}
-  \end{subfigure}
-  \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\textwidth]{seed_ACH21_segment2.pdf}
-  \caption{Found 13 Unique States}\label{fig:segment3}
-  \end{subfigure}
-  \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\textwidth]{seed_ACH21_segment3.pdf}
-  \caption{Found 12 Unique States}\label{fig:segment4}
-  \end{subfigure}
-  \begin{subfigure}{1\textwidth}
-  \includegraphics[width=\textwidth]{seed_ACH21_full.pdf}
-  \caption{Initial state sequence seeded with states found in (a)--(d)}\label{fig:full}
-  \end{subfigure}
-  \caption{In (a--d), we show the state sequence resulting from 5 iterations
-  of the IHMM on each of the four quarters of the center-of-mass trajectory in
-  (e) after splitting it into 4 separate segments. We use the concatenation 
-  of the four state sequences as the initial sequence for the IHMM run on the 
-  fully trajectory in (e).
-  }\label{fig:seed_sequence}
-  \end{figure}
-
   \section{Deviations of the IHMM from Molecular Motion}\label{section:shorttimes_msd}
@@
 
+  \section{Clustered Parameters}\label{section:clustered_parmeters}
+
+  We can begin to hypothesize mechanisms by studying the behaviors defined by the 
+  state parameters. In Figure~\ref{fig:common_states_lines}, we plot representative 
+  dynamics of each of the five most visited states (see Figure~\ref{M-fig:prevalence}
+  of the main text). The states exhibit a range of autoregressive and trapping 
+  behavior throughout the membrane pores.
+
+  Since the radial means are weighted averages of the states used to parameterize
+  each cluster, for interpretive purposes, it is important to recognize that the means
+  only provide clues towards the general location of the solute. For example, the 
+  radial mean of state 3 is 1.4 nm from the pore center. However, inspection of 
+  Figure~\ref{fig:clustered_traj_MET} suggests that this type of behavior actually
+  occurs radially throughout the pore. There are instances of state 3 less than 1 nm
+  from the pore center and more than 2 nm from the pore center. In this case, the 
+  radial mean only suggests that this type of behavior happens in both regions somewhat
+  equally.
+
+  Solutes exhibit a range of autoregressive behavior as shown by the representative 
+  solute trajectories in Figure~\ref{fig:common_states_lines} and the scatter
+  plot in Figure~\ref{fig:A_sigma_scatter}. In most cases, the eigenvalues of $A$ and
+  $\Sigma$ appear nearly paired in their radial and axial dimensions, which implies 
+  nearly symmetric behavior with off-diagonals both matrices near zero. The most 
+  notable exception is state 3, which has a much higher radial eigenvalue of the 
+  covariance matrix. Both eigenvalues of state 3's covariance are actually quite
+  large. This implies relatively large fluctuations in the $z$ direction and even
+  bigger fluctuations in the $r$ direction. All states have slightly lower covariance
+  in the axial direction. It's likely easier for solutes to move laterally rather 
+  than to move up through the alkane chains. States 3 and 4 show a strong previous-hop
+  dependence (high $A$) while the rest of the states have a somewhat weaker dependence.
+
+  Solutes stay trapped for various lengths of time. On average, state 4 has the longest 
+  dwell times and state 3 has the shortest dwell times while the rest have intermediate
+  dwell times. This is somewhat supported by inspection of Figure~\ref{fig:clustered_traj_MET},
+  however. The expected dwell times of the clusters incorporate all 24 trajectories.
+
+  % BJC4: Not sure if this is useful.
+  % MRS: it does give a good summary. But you should make it clear how you selected these 5.
+  % MRS: it's implied in one of the figures, but should be stated explicitly
+%  By examining the parameters, it is now easier to describe the state behavior.
+%  \begin{enumerate}[label={State \theenumi :}, leftmargin=3.5\parindent]
+%     \item This state has intermediate dwell times with high past-hop dependence.
+%     The radial mean and evidence from Figure~\ref{fig:clustered_traj_MET} suggests
+%     %MRS: ``tail and pore region'' sounds the same as ``everywhere''.
+%     that this state is common in the tail and pore region.
+%     \item This state seems to occur exclusively in the tail region based on its radial
+%     mean. Its fluctuations are small and there is little past hop dependence
+%     \item This is likely a hopping state that strongly contribute to the solute's MSD. 
+%     It is short lived and takes very large hops. This type of behavior is exhibited 
+%     %MRS: ``near and far'' also sounds like everywhere 
+%     near and far from the pore center as discussed earlier.
+%     \item This is a trapping state with a strong dependence on its previous fluctuation.
+%     Evidence from Figure~\ref{fig:clustered_traj_MET} and a radial mean of 1.8 suggest
+%     that it tends to occur at intermediate distances from the pore center.
+%     \item This is an intermediate-length trapping state that occurs close to the pore
+%     center. It's fluctuations are tight and relatively independent of its previous 
+%     fluctuation.
+%  \end{enumerate}
+
+  \begin{figure}
+  \centering
+  \begin{subfigure}{0.58\textwidth}
+  \includegraphics[width=\textwidth]{common_states.pdf}
+  \caption{}\label{fig:common_states_lines}
+  \end{subfigure}
+  \begin{subfigure}{0.41\textwidth}
+  \includegraphics[width=\textwidth]{A_sigma_scatter.pdf}
+  \caption{}\label{fig:A_sigma_scatter}
+  \includegraphics[width=\textwidth]{dwell_times.pdf}
+  \caption{}\label{fig:dwell_times}
+  \end{subfigure}
+  \caption{The 5 most visited states by methanol show a range of dynamical behavior. In 
+  (a), we show representative dynamics of these states. All time series have a mean of zero and are
+  shifted to put the mean in line with the $y$-axis labels for the purpose of visualizing them.
+  The $y$-axis labels of the $r$ coordinate plot specify the radial mean of each clustered 
+  state. All of the states pictured appear in the trajectory shown in 
+  Figure~\ref{M-fig:clustered_traj_MET} of the main text and are colored to match.
+  (b) We can begin to understand the solute behaviors demonstrated in (a) by understanding their VAR 
+  parameters. Higher values of $\lambda_{\Sigma}$ generally are indicative of large fluctuations
+  and higher values of $\lambda_A$ indicate strong previous-hop dependence of the fluctuations.
+  (c) Using Equation~\ref{M-eqn:dwell_times} of the main text, we estimated the expected time spent within each 
+  of the states.
+  }\label{fig:common_states_MET}
+  \end{figure}
+
 \end{document}

### 2020-05-21 Ben_Manuscripts/hdphmm/Draft.tex
Almost complete draft. Added new figures

@@
   we apply the sticky hierarchical Dirichlet process autoregressive hidden Markov model
-  (HPD-AR-HMM) to solute center-of-mass trajectories generated from long molecular dynamics 
-  simulations in a cross-linked inverted hexagonal phase lyotropic liquid crystal
-  (LLC) membrane in order to automatically detect a variety of solute dynamical states
+  (HPD-AR-HMM) to solute center-of-mass trajectories generated from long molecular dynamics (MD)
+  simulations in a cross-linked inverted hexagonal phase lyotropic liquid crystal (LLC)
+  membrane in order to automatically detect a variety of solute dynamical states
   which can be further explained in terms of solute-membrane interactions.
@@
   prevalent clusters in order to relate their parameters to physical interactions between 
-  solutes and the membrane. 
-  Along with parameters of individual states, the HDP-AR-HMM simultaneously infers a transition
-  matrix which allows us to stochastically propagate solute behavior from all of the 
-  independent trajectories onto much longer time scales while still preserving the 
-  qualitative behavior characteristic of the MD trajectories. This affords a direct 
-  connection to important macroscopic observables used to characterize performance like
-  solute flux and selectivity.
+  solutes and the membrane. Along with parameters of individual states, the HDP-AR-HMM 
+  simultaneously infers a transition matrix which allows us to stochastically propagate
+  solute behavior from all of the independent trajectories onto arbitrary length time 
+  scales while still preserving the qualitative behavior characteristic of the MD 
+  trajectories. This affords a direct connection to important macroscopic observables 
+  used to characterize performance like solute flux and selectivity.
 
@@
   municipal water supplies, recovering valuable dissolved species from 
-  waste stream and creating breathable barriers to harmful contaminants are just a
+  waste streams and creating breathable barriers to harmful contaminants are just a
   subset of the broad range of applications for selective membrane separations.~\cite{fritzmann_state---art_2007,fonseca_couto_critical_2018,dischinger_evaluation_2019,ramaseshan_functionalized_2006}
@@
   as VAR processes and we will refer to our model as an application of the 
-  sticky HDP-AR-HMM in order to maintaining its distinction from the even more
+  sticky HDP-AR-HMM in order to maintain its distinction from the even more
   general sticky HDP-SLDS models.
@@
   time series trajectories which enables projections of MD simulations on 
-  much longer time scales.
+  arbitrary length time scales.
 
@@
   exhibited by MD. One can project these realizations onto much longer 
-  timescales with computational ease extending into timescales where 
+  time scales with computational ease extending into time scales where 
   regular diffusive behavior again occurs.
@@
 
-  Each solute system was simulated for 5 $\mu$s of molecular dynamics simulation. We
-  used a time step of 2 fs at a pressure of 1 bar and temperature of 300K controlled
-  by the semi-isotropic Parrinello-Rahman 
+  Each solute system was simulated for 5 $\mu$s using MD. We used a time step of 2 
+  fs at a pressure of 1 bar and temperature of 300K controlled by the semi-isotropic 
+  Parrinello-Rahman 
   %MRS: just wondering, was this semiisotropic, or isotropic?  If isotropic, do we know how different the diagonals of the pressure tensor were (since the system is not totally isotropic)
@@
   the membrane pore. By working in Cartesian coordinates, we avoid mathematical 
-  complexity introduced by change of coordinates into cylindrical coordinates while
+  complexity introduced by changing into cylindrical coordinates while
   estimating the state sequence.
@@
   We used a conjugate matrix-normal inverse-Wishart (MNIW) prior on parameters 
-  $A$ and $\Sigma$ and a Gaussian prior on $\mathbf{c}$ in order to infer their 
+  $A$ and $\Sigma$ and a Gaussian prior on $\mathbf{c}$ in order to efficiently infer their 
   values.~\cite{fox_nonparametric_2009}
@@
   the state sequence is relatively stable since the inferred parameters are 
-  sensitive to the inputs to the MNIW conjugate priors. In states with a low number
-  of emissions, the boundaries of the state segments fluctuate which can lead to high
-  variance in the $A$ and $\Sigma$ parameters. In these cases, plateauing of the mean in each dimension 
-  tends to be a more reliable indicator of convergence (see 
+  sensitive to the inputs to the MNIW conjugate priors. The precise boundaries of 
+  the state segments can fluctuate, therefore in states with a low number of 
+  emissions,  the variance in $A$ and $\Sigma$ parameters. In these cases, plateauing
+  of the mean in each dimension tends to be a more reliable indicator of convergence (see 
   Figure~\ref{S-fig:convergence3d} of the Supporting Information).
@@
   Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. In 
-  Section~\ref{S-section:prior_guesses} of the Supporting Information we outline our 
-  algorithmic method for choosing reliable prior parameters. We provide additional 
-  practical tips for initialization in Section~\ref{S-section:fitting_tips}
-  of the Supporting Information.
+  Section~\ref{S-section:fitting_tips} of the Supporting Information we outline our 
+  algorithmic method for choosing reliable prior parameters in addition to other 
+  practical tips for initialization.
 
@@
   We clustered like parameter sets in order to reduce the state space to
-  a more easily interpretable size. For each solute studied, we identified 200-325
-  independent states, each with separate VAR(1) parameters. Many of these states
+  a more easily interpretable size. For each solute studied, we identified approximately 
+  300-500 independent states, each with separate VAR(1) parameters. Many of these states
   exhibit very similar dynamical behavior except their mean levels in each dimension
@@
   and $\Sigma$ capture the correlation and size of fluctuations. $T_{ii}$ is directly
-  related to the average time spent in each state. The distance from the closest pore 
+  related to the expected time spent in each state. The distance from the closest pore 
   center is likely meaningful since the membrane is radially inhomogeneous from each 
@@
   There are alternative ways to cluster the data dependent on one's goals. Our goal is
-  to derive the simplest set of parameter which adequately describe solute motion. 
+  to derive the simplest set of parameters which adequately describe solute motion. 
   However, one may want a more detailed understand of specific dimensions of the 
@@
   First, we modified the ($x$, $y$, $z$) solute trajectories so that they had a 
-  mean of zero, leaving only the fluctuations. Next, we took advantage of the
+  mean of zero, leaving only the fluctuations. We took advantage of the
   rotational invariance of the system by rotating the coordinates about the pore 
-  axis such that the mean vector of each separate segment was aligned with the 
-  $x$ axis. Next, we subtracted the means from each separate segment in the $x$ 
-  and $z$ dimensions, with the mean in $y$ being zeroed by the rotation. We used
+  axis such that the mean ($x$, $y$) vector of each separate segment was aligned with the 
+  $x$ axis, forcing the $y$ component to zero. Next, we subtracted the means from 
+  each separate segment in the $x$ and $z$ dimensions. We used
   the inference component of the HDP-AR-HMM algorithm on this modified trajectory to 
@@
   \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
-  	\item For each trial, we generated 24 stochastic trajectories, one from each of
-  	the 24 independent HDP-AR-HMM models. The result of the bootstrap trial is the mean
-  	of the MSDs calculated from each trajectory. 
+  	\item For each bootstrap trial, we generated 24 stochastic trajectories, one from
+  	each of the 24 independent HDP-AR-HMM models. The result of the trial is the mean
+  	of the MSDs calculated from each trajectory constituting the ensemble. 
     \item We generated an ensemble of 1000 independent stochastic trajectories using
@@
   It can be shown on time scales where motion is uncorrelated, that the diffusion
-  constant is linearly proportional to the slope of the MSD curve:~\cite{einstein_investigations_1956}
+  constant is proportional to the slope of the linear region of the MSD 
+  curve:~\cite{einstein_investigations_1956}
   \begin{equation}
@@
   \end{equation}
-  where $n$ is the number of spatial dimensions (1 in our case). Since the MSD
-  of the realizations of our models enters a linear regime, we can estimate 
-  diffusion constants 
-  % MRS: maybe can say what the timescale of the linear regime, and how much 
-  % longer the stochastic realizations are?
-  based on the slope of the linear region of the predicted MSD curves.
+  where $n$ is the number of spatial dimensions (1 in our case). In general, the 
+  MSD of the realizations of our models enters a linear regime near a 5 ns time lag
+  (see Figure~\ref{S-fig:MET_nclusters} of the Supporting Information for example).
+  Since MSD sampling decreases with increasing time lag, longer trajectory 
+  realizations help to extend the linear region.
+  %BJC: need to confirm these details
+  For all solutes, we generated 200 ensembles of 24 10 $\mu s$ trajectories and 
+  estimated $D$ from the slope fit between 5 ns and 1000 ns. We used weighted 
+  least squares to fit the slope with weights determined by the number of time 
+  lags used to compute the average ($T - \tau$ in equation~\ref{eqn:tamsd}). 
+  We bootstrapped error bars for the final reported selectivities. For each 
+  bootstrap trial, we sampled the 200 trajectory ensembles with replacement, 
+  averaging the mean MSD curves calculated from each ensemble and then calculating its 
+  slope to create a distribution of $D$ values. We report the mean and standard
+  error of the distribution of $D$.
 
@@
   We applied the HDP-AR-HMM independently to all 24 trajectories of each of the four solutes studied.
-  The number of states found for each trajectory varied between 5 and 30.  %BJC4: MET: (5, 28), need to finalized
-  Figure~\ref{fig:rz_unclustered}, shows the state sequence determined by the HDP-AR-HMM for
+  The number of states found for each trajectory varied between 2 and 45.  %BJC4: MET: (5, 28), URE: (5, 45), ACH: (2, 25), GCL: (7, 35)
+  Figure~\ref{fig:rz_unclustered} shows the state sequence determined by the HDP-AR-HMM for
   an example methanol trajectory. The model distinguishes many of the states due to 
@@
   \includegraphics[width=\textwidth]{rz_unclustered_MET.pdf}
-  \caption{The HDP-AR-HMM found 24 distinct VAR(1) states in this representative methanol trajectory.
+  \caption{The HDP-AR-HMM found 20 distinct VAR(1) states in this representative methanol trajectory.
   We performed the parameterization in 3D Cartesian coordinates, but for this figure, we 
@@
   As shown in Figure~\ref{fig:qualitative_unclustered}, realizations of our model 
-  produce trajectories that show qualitatively similar hopping and trapping 
-  behavior to the MD trajectories to which they were fit. It is important that our
+  produce trajectories with hopping and trapping behavior that is qualitatively 
+  similar to the MD trajectories to which they were fit. It is important that our
   model reproduces this behavior so that we can have confidence in its usefulness
@@
   \includegraphics[width=\textwidth]{qualitative_unclustered_MET2.pdf}
-  \caption{We can use realizations of the HDP-AR-HMM to generate trajectories which 
-  bear qualitative resemblance to the MD trajectories. We used the parameters 
-  of the HDP-AR-HMM, whose state segments are visualized in 
-  Figure~\ref{fig:rz_unclustered}, in order to construct an ensemble of 
-  characteristic trajectories. Solute trajectories generated with
-  the HDP-AR-HMM (blue) show the same hopping and trapping behavior exhibited by 
-  MD (black).
+  \caption{We used the parameters of the HDP-AR-HMM, whose state segments are 
+  visualized in Figure~\ref{fig:rz_unclustered}, in order to construct an 
+  ensemble of characteristic trajectories. The stochastic trajectories 
+  generated by the parameters of the HDP-AR-HMM (blue) show the same hopping
+  and trapping behavior exhibited by MD (black).
+%  We can use realizations of the HDP-AR-HMM to generate trajectories which 
+%  bear qualitative resemblance to the MD trajectories. 
   }\label{fig:qualitative_unclustered}
@@
   adequately parameterize an HDP-AR-HMM which reproduced the uncharacteristic
-  behavior. (see SI)  %BJC4: TODO
-  On long timescales, the model appear to have the same slope as the MD 
-  trajectory.
-
+  behavior (see SI).
+%BJC5: TODO.
+There are a couple trajectories I want to show have very high MSDs because all the hops are in one direction along the pore.
+The curves look superdiffusive.
+I think on longer timescales, this wouldn't happen.
+I'll also show the MD MSD curves without the 'outliers' in the SI.
+  On long time scales, the model's MSD appear to have a slope similar to the MD 
+  MSD.
+
+  %BJC5: need to update legend to say HDP-AR-HMM
   \begin{figure}
@@
   \end{subfigure}
-  \caption{The MD MSDs (black) of methanol and urea are under-predicted by 
-  the HDP-AR-HMM (orange), while the predictions match within uncertainty for ethylene
-  glycol and acetic acid}\label{fig:unclustered_msds}
+  \caption{For methanol, ethylene glycol and acetic acid, the MD MSDs (black) and the MSDs
+  calculated from realizations of the HDP-AR-HMM match within uncertainty. The MD MSD of
+  urea is under-predicted by the HDP-AR-HMM.}\label{fig:unclustered_msds}
   \end{figure}
@@
   %MRS: seems odd not at least mention clustering here.
-
-  Since we can generate trajectories that share features similar to MD simulations, 
-  it is now reasonable to project solute behavior onto much longer time scales. The 
-  HDP-AR-HMM MSD predictions quickly enter a linear regime, therefore we can project
-  long timescale MSDs based on the predicted diffusion constant as described in 
-  Section~\ref{method:selectivity}.
-
-  % BJC4: figure here
-
-  % BJC4: some kind of brief selectivity analysis here.
+  %BJC5: I haven't talked about clustering yet. Should this section get moved later? I think it leads into the next section well here.
+
+  Since we can generate trajectories that share the qualitative and quantitative
+  features of our MD simulations, we can now use realizations of the HDP-AR-HMM
+  in order to estimate selectivity as described in Section~\ref{method:selectivity}.
+  In Figure~\ref{fig:selectivity}, we plot the selectivities estimated by our
+  models for all possible pairs of solutes.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{selectivity.pdf}
+  \caption{Of the solutes studied, the current generation of H\textsubscript{II}
+  LLC membranes may have the most success selectively removing acetic acid and,
+  to a lesser extent, urea from solution containing either ethylene glycol or 
+  methanol.
+  }\label{fig:selectivity}
+  \end{figure}
+
+  The data suggests that the particular LLC membrane studied in this work is
+  capable of selectively separating urea and acetic acid from ethylene glycol
+  and methanol. Ethylene glycol and methanol have comparable diffusivities
+  while urea and acetic acid have much lower diffusivities.
+
+  If we can understand the mechanisms that lead to the various observed transport
+  rates, one may be able to redesign the LLC monomers in order to influence solute
+  selectivities. For example, it is not obvious why ethylene glycol and methanol
+  have similar transport rates. Ethylene glycol is a larger molecule with a 
+  molecular weight about twice that of methanol. Their relative diffusivities are 
+  not consistent with the inverse molecular size relationship implied by the 
+  Stokes-Einstein equation.~\cite{gierer_molekulare_1953} The HDP-AR-HMM may 
+  help us pinpoint the differences in their transport behavior.
 
@@
   shared across all trajectories. For the trajectory in this figure, we reduced
-  the total number of states from 24 (see Figure~\ref{fig:rz_unclustered}) to
+  the total number of states from 20 (see Figure~\ref{fig:rz_unclustered}) to
   5.}\label{fig:clustered_traj_MET}
@@
   seen in our MD trajectories. (b) MSD predictions by clustered parameter sets consistently
-  under-predict MD MSD. They appear to do a better job of predicting MSDs as the number
+  under-predict the MD MSD. They appear to do a better job of predicting MSDs as the number
   of clusters increases.}\label{fig:clustered_dynamics}
@@
 %  dwells times.
-  However, we do not go too far in order to prevent over-fitting.
+  However, we did not pursue this too far in order to avoid over-fitting the data.
   %BJC5: maybe an SI figure showing some different approaches
@@
   trajectories (Figure~\ref{fig:prevalence}). All of which are present in 
-  Figure~\ref{fig:clustered_traj_MET}. Although a majority of the solutes
-  visit these 5 dominant states the amount of time spent in each varies widely.
+  Figure~\ref{fig:clustered_traj_MET}.
+
+  %Although a majority of the solutes
+  %visit these 5 dominant states the amount of time spent in each varies widely.
 
@@
   \caption{5 out of the 10 clustered states are visited by 15 or more of the solute
-  trajectories. The solutes spend varying amounts of time in each of these states.
+  trajectories. Although a majority of the solutes visit these 5 dominant states, the
+  amount of time spent in each varies widely. 
+  % The solutes spend varying amounts of time in each of these states.
   }
@@
   \begin{enumerate}[label={State \theenumi :}, leftmargin=3.5\parindent]
-     \item This state has intermediate dwell times with high past-hop dependence (high entries of $A$).
-     The radial mean and evidence from Figure~\ref{fig:clustered_traj_MET} suggests
-     %MRS: ``tail and pore region'' sounds the same as ``everywhere''.
-     that this state is common in the tail and pore region.
-     \item This state seems to occur exclusively in the tail region based on its radial
-     mean. Its fluctuations are small and there is little past hop dependence
-     \item This is likely a hopping state that strongly contribute to the solute's MSD. 
-     It is short lived and takes very large hops. This type of behavior is exhibited 
-     %MRS: ``near and far'' also sounds like everywhere 
-     near and far from the pore center as discussed earlier.
-     \item This is a trapping state with a strong dependence on its previous fluctuation.
-     Evidence from Figure~\ref{fig:clustered_traj_MET} and a radial mean of 1.8 suggest
-     that it tends to occur at intermediate distances from the pore center.
-     \item This is an intermediate-length trapping state that occurs close to the pore
-     center. It's fluctuations are tight and relatively independent of its previous 
+     \item This state has intermediate dwell times with high past-hop dependence (high
+     entries of $A$). The cluster's radial mean is 1.5 nm which is about halfway between
+     the pore center and tail ends. Evidence from Figure~\ref{fig:clustered_traj_MET} 
+     suggests that this state is common both close to the pore center and in the tail
+     and region.
+     % MRS: ``tail and pore region'' sounds the same as ``everywhere''.
+     % BJC5: That's kind of what I mean. Behavior is similar near pore center and far
+     % from pore center. Half happen at pore, half happen in tails, average r is 1.5 nm
+     \item This state's radial mean of 2.4 nm implies that it occurs exclusively in the
+     tail region based. Its fluctuations are small and there is little past hop dependence.
+     \item This is likely a hopping state that strongly contributes to the solute's MSD. 
+     It is short lived and has large fluctuations which often results in very large hops.
+     Like State 1, we see this type of behavior near the pore center and near the ends of the tails.
+     \item This is a trapping state, having the longest expected dwell time among the dominant
+     states, with a strong dependence on its previous fluctuation. Evidence from 
+     Figure~\ref{fig:clustered_traj_MET} and a radial mean of 1.8 suggest that it tends to
+     occur at intermediate distances from the pore center with perhaps a higher tendency
+     to occur deeper within the tails.
+     \item This is an intermediate-length trapping state that occurs 0.9 nm from the pore 
+     center on average. It's fluctuations are tight and relatively independent of its previous 
      fluctuation.
@@
 
-  \textit{Relating Parameters to Solute-Membrane Interactions}: Based on the
-  molecules and ions which constitute the membrane, it is straightforward to 
-  hypothesize two types interactions that might occur.
-  \begin{itemize}  
-    \item All of the solutes are polar and have hydrogen bond donating and 
-    accepting groups. 
-    \item The monomers have 10 oxygen atoms distributed from head to tail that are 
-    capable of accepting hydrogen bonds. 
-    \item Also, the ionic bond between the head groups and sodium ions can
-    be easily broken since both components can be stabilized by surrounding 
-    water molecules and solutes.
-    \item Therefore, it is logical to search for hydrogen bonding interactions
-    and solute association with sodium ions.
-  \end{itemize}
-  %MRS: above, start with the last point; state what the interactions are, and then give the reasoning.
+  \textit{Relating Parameters to Solute-Membrane Interactions}: Based on the molecules
+  and ions which constitute this system, it is logical to search for hydrogen bonding
+  interactions and solute association with sodium ions. All of the solutes are
+  polar and have hydrogen bond donating and accepting groups. The monomers 
+  have 10 oxygen atoms distributed from head to tail that are capable of 
+  accepting hydrogen bonds. The ionic bond between the head groups and sodium ions 
+  can be easily broken since both components can be stabilized by surrounding 
+  water molecules and solutes
+
   For methanol, hydrogen bonding is a much more dominant interaction than sodium
-  ion association. 
-  \begin{itemize}
-    \item In Figure~\ref{fig:hbond_fractions}, we show that methanol participates
-    in hydrogen bonds to various parts of the monomer between 27 and 45\% of the
-    total time it occupies the dominant states.
-    \item Methanol associates with sodium ions less than 10\% of the time in 
-    dominant states.
-  \end{itemize}
+  ion association. In Figure~\ref{fig:hbond_fractions}, we show that methanol 
+  participates in hydrogen bonds to various parts of the monomer between 27 and
+  45\% of the total time it occupies the dominant states. Methanol associates 
+  with sodium ions less than 10\% of the time in dominant states.
 
   The distribution of types of hydrogen bonds and associated hydrogen bond lifetimes
-  varies by dominant state.
-  \begin{itemize}
-    \item States 1 and 2 are dominated by hydrogen bonds to the head groups and, to 
-    a smaller extent, the ether linkages.
-    \item State 1 methanol molecules that donate hydrogen bonds to the tail oxygen 
-    atoms exhibit by far the longest hydrogen bond lifetimes among all states.
-    \item States 3 and 4 hydrogen bond to all regions of the monomer relatively 
-    evenly, which is consistent with our earlier observation that states 3 and 4
-    are representative of behavior seen radially throughout the membrane pores.
-    \item State 3 has the lowest hydrogen bond and sodium association lifetimes 
-    which is consistent with its short dwell times. These are fleeting interactions
-    since it is likely a jumping state.
-    \item Methanol molecules in state 5 hydrogen bond almost exclusively to the 
-    carboxylate head groups and ether linkages which is consistent with the radial
-    mean of the cluster.
-  \end{itemize}
+  varies by dominant state. States 1 and 2 are dominated by hydrogen bonds to the 
+  head groups and, to a smaller extent, the ether linkages. State 1 methanol
+  molecules that donate hydrogen bonds to the tail oxygen atoms exhibit by far 
+  the longest hydrogen bond lifetimes among all states. States 3 and 4 hydrogen 
+  bond to all regions of the monomer relatively evenly, which is consistent with
+  our earlier observation that states 3 and 4 are representative of behavior 
+  seen radially throughout the membrane pores. State 3 has the lowest hydrogen 
+  bond and sodium association lifetimes which is consistent with its short dwell
+  times. These are fleeting interactions since it is likely a jumping state.
+  Methanol molecules in state 5 hydrogen bond almost exclusively to the carboxylate
+  head groups and ether linkages which is consistent with the radial mean of the
+  cluster.
 
@@
 
-  The local number density of heavy atoms surrounding solutes help round out methanol's
-  mechanistic picture.
-  \begin{itemize}
-    \item Although hydrogen bonding interactions are relatively frequent, methanol molecules
-    are unbound by any measurable electrostatic interactions about half or more of the 
-    simulation time.  
-    %MRS: this above doesn't support the thesis statement?
-    \item Figure~\ref{fig:local_densities} helps to illustrate how the local density of 
-    membrane components can aid in solute entrapment.
-    \item When solutes experience long trapping times, the local number density of heavy 
-    atoms is larger.
-    \item Even when hydrogen bonds break, surrounding alkane density likely helps keep
-    the solutes in place allowing them to eventually reform. This can happen deep in the
-    tails or close to the monomer head groups.
-    \item Methanol molecules which experience State 3 have by far the smallest local 
-    number density which is likely responsible for their mobility, as suggested by the state's
-    large covariance.
-  \end{itemize}
+  \textit{Comparison of Solute Behavior}: We can apply a similar analysis to the other 
+  solutes in this study and learn new information by comparing their behavior.
+
+  The size and chemical functionality of the solutes dictates the interactions which
+  influence solute transport. In Figure~\ref{fig:hbonds_assoc_summary}, we show that the
+  solutes donate hydrogen bonds and associate with sodium ions to varying degrees.
+  In fact methanol, by far, interacts the least by these mechanisms. This is likely 
+  because methanol is very small and it is easier for it to partition into the tail
+  region where there are fewer groups with which it can interact (see Figure~\ref{fig:rdf_summary}).
+  Acetic acid, urea and ethylene glycol are slightly larger than methanol and contain 
+  multiple polar substituents which stabilize them closer to the pore region.
+  These three solutes also participate in significantly more sodium ion association. 
+  In our previous work, we showed that sodium ions frequently associate with the 
+  carbonyl groups of acetic acid and urea.
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{local_densities.pdf}
-  \caption{We measured the local number density of heavy atoms surrounding solutes in each
-  state. In blue, we plot the local number density experienced by solutes averaged over all
-  frames in which the solute occupied the given state. We broke down this overall average 
-  number density into number densities measured from instances when the state is occupied 
-  for long (orange) versus short(red) dwell time states. We define define `long' dwells times
-  as the 50th percentile of all dwell times in the given state, and short as all others. It
-  is clear that solutes which experience longer dwells times are also surrounded by more 
-  heavy atoms on average.}\label{fig:local_densities}
-  \end{figure}
-
-  \subsubsection*{Comparison of Solute Behavior}
-
-  We can apply a similar analysis to the other solutes in this study. We can likely
-  learn new information through comparison of solute behavior with metrics based on
-  the chemical intuition gained by studying methanol.
-
-  The size and chemical functionality of the solutes dictates the interactions which
-  influence solute transport.
-  \begin{itemize}
-    \item In Figure~\ref{fig:hbonds_assoc_summary}, we show that the solutes donate
-    hydrogen bonds and associate with sodium ions to varying degrees.
-    \item In fact methanol, by far, interacts the least by these mechanisms.
-    \item This is likely because methanol is very small and it is easier for it to partition
-    into the tail region where there are fewer groups with which it can interact (see
-    Figure~\ref{fig:rdf_summary}).
-    \item Acetic acid, urea and ethylene glycol are slightly larger than methanol
-    and contain multiple polar substituents which stabilize them closer to the 
-    pore region.
-    \item These three solutes also participate in significantly more sodium ion
-    association. 
-    \item In our previous work, we showed that the sodium ions frequently associate
-    with the carbonyl groups of acetic acid and urea.
-  \end{itemize}
-
-  \begin{figure}
-  \centering
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.49\textwidth}
   \includegraphics[width=\textwidth]{hbonds_assoc_summary.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.49\textwidth}
   \includegraphics[width=\textwidth]{rdf_summary.pdf}
@@
   \end{subfigure}
-  \begin{subfigure}{0.325\textwidth}
+  \begin{subfigure}{0.49\textwidth}
   \includegraphics[width=\textwidth]{dwell_time_summary.pdf}
   \caption{}\label{fig:dwell_time_summary}
+  \end{subfigure}
+  \begin{subfigure}{0.49\textwidth}
+  \includegraphics[width=\textwidth]{density_comparison.pdf}
+  \caption{}\label{fig:density_comparison}
   \end{subfigure}
@@
 
-  Solutes with dominant clusters characterized by long dwell times tend to 
-  have lower MSDs.
-  \begin{itemize}
-    \item In Figure~\ref{fig:dwell_time_summary}, we plot the expected dwell
+  Solutes with dominant states characterized by long dwell times tend to 
+  have lower MSDs. In Figure~\ref{fig:dwell_time_summary}, we plot the expected dwell
   time of each solute in the dominant state which has the the highest 
-    self-transition probability. 
-    \item The trend in MSDs is inversely related to the trend in maximum
-    expected dwell times.
-    \item Both acetic acid and urea participate in many hydrogen bonds and
-    sodium ion association interactions and the states visited by both solutes
-    have similar distributions of radial means, however acetic acid is 
-    subject to much longer dwell times, and hence a lower MSD.
-    % BJC4: I could dig further into this. Not sure if worth it.
-    \item This may be because acetic acid is a stronger hydrogen bond donor
-    than urea. 
-    \item Could also be that the urea is still mobile while paired with sodium ions.
-  \end{itemize}
+  self-transition probability. We define the dominant states as any states that
+  are visited by more than half of the solute trajectories. The trend in MSDs is
+  inversely related to the trend in maximum expected dwell times. Both acetic acid
+  and urea participate in many hydrogen bonds and sodium ion association interactions
+  and the states visited by both solutes have similar distributions of radial means,
+  however acetic acid is subject to much longer dwell times, and hence a lower MSD. 
+  This may be because acetic acid is a stronger hydrogen bond donor than urea.
+
+  In addition to hydrogen bonding and sodium ion association, the local density 
+  of heavy atoms experienced by each solute may play a large role in the length
+  of solute entrapment. In Figure~\ref{fig:density_comparison}, we show that the
+  expected dwell time of solutes in dominant states tends to increase with 
+  local density. High local density combined with polar and electrostatic interactions
+  act cooperatively to keep solutes in place.
 
@@
 
-  Although we showcase this modeling approach by example, but it is important to
+  Although we showcase this modeling approach by example, it is important to
   recognize the generality of this analysis, especially in the context of molecular

### 2020-05-21 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Almost complete draft. Added new figures

@@
 
-  \section{Choosing Prior Parameters}\label{section:prior_guesses}
+  \section{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
 
-  The states identified by the IHMM are heavily influenced by the Gaussian prior
-  placed on $\mathbf{c}$ in Equation~\ref{M-eqn:var} of the main text. The 
-  entries of $A$ and $\Sigma$ do not vary over a wide range, so the final
-  parameters were relatively insensitive to the priors. In order to 
-  maximally automate the IHMM procedure, we attempted to parameterize the
+  \textit{Choosing Prior Parameters}: The states identified by the IHMM are 
+  heavily influenced by the Gaussian prior placed on $\mathbf{c}$ in 
+  Equation~\ref{M-eqn:var} of the main text. The entries of $A$ and $\Sigma$
+  do not vary over a wide range, so the final parameters were relatively 
+  insensitive to the priors. In order to maximally automate the IHMM procedure,
+  we attempted to parameterize the
   prior on $\mathbf{c}$ in an intelligent way. The prior parameters should
@@
   \pagebreak
-
-  \section{Clustering}\label{section:clustering}
-
-  \subsection{Agglomerative Clustering Versus Gaussian Mixture Models}\label{section:agglomerative}
-
-  % BJC: will show Gaussian mixture model which has a cluster engulfing another cluster, so
-  % it's tails are on both sides of the center cluster.
-
-  \begin{figure}[h]
-  \centering
-  \begin{subfigure}{0.95\textwidth}
-  \includegraphics[width=\textwidth]{bayesian_A.pdf}
-  \caption{Bayesian Gaussian mixture model}\label{fig:bayesian_A}
-  \end{subfigure}
-  \begin{subfigure}{0.95\textwidth}
-  \includegraphics[width=\textwidth]{agglomerative_A.pdf}
-  \caption{Agglomerative Clustering}\label{fig:agglomerative_A}
-  \end{subfigure}
-  \caption{To reduce the state space, we prefer agglomerative clustering over Bayesian
-  Gaussian mixture modeling. In the plots above we show the results of clustering the
-  diagonal entries of the autoregressive coefficient matrices, $A$, of methanol. (a) 
-  Bayesian Gaussian mixture models tend to delocalize the clusters in parameter space
-  since the Gaussians can overlap. Agglomerative clustering prevents overlap of 
-  clusters and ensures that all states within each cluster have similar parameters.
-  }\label{fig:clustering_choice}
-  \end{figure}
-
-  \newpage
-
-  \section{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
 
@@
   \end{figure}
+
+  \section{Clustering}\label{section:clustering}
+
+  \subsection{Agglomerative Clustering Versus Gaussian Mixture Models}\label{section:agglomerative}
+
+  % BJC: will show Gaussian mixture model which has a cluster engulfing another cluster, so
+  % it's tails are on both sides of the center cluster.
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.95\textwidth}
+  \includegraphics[width=\textwidth]{bayesian_A.pdf}
+  \caption{Bayesian Gaussian mixture model}\label{fig:bayesian_A}
+  \end{subfigure}
+  \begin{subfigure}{0.95\textwidth}
+  \includegraphics[width=\textwidth]{agglomerative_A.pdf}
+  \caption{Agglomerative Clustering}\label{fig:agglomerative_A}
+  \end{subfigure}
+  \caption{To reduce the state space, we prefer agglomerative clustering over Bayesian
+  Gaussian mixture modeling. In the plots above we show the results of clustering the
+  diagonal entries of the autoregressive coefficient matrices, $A$, of methanol. (a) 
+  Bayesian Gaussian mixture models tend to delocalize the clusters in parameter space
+  since the Gaussians can overlap. Agglomerative clustering prevents overlap of 
+  clusters and ensures that all states within each cluster have similar parameters.
+  }\label{fig:clustering_choice}
+  \end{figure}
+
+  \newpage
 
@@
 
+  The local number density of heavy atoms surrounding solutes help round out methanol's
+  mechanistic picture. Although hydrogen bonding interactions are relatively frequent,
+  methanol molecules are unbound by any measurable electrostatic interactions about 
+  half or more of the simulation time. Figure~\ref{fig:local_densities} helps to 
+  illustrate how the local density of membrane components can aid in solute entrapment.
+  When solutes experience long trapping times, the local number density of heavy atoms
+  is larger. Even when hydrogen bonds break, surrounding alkane density likely helps 
+  keep the solutes in place allowing them to eventually reform. This can happen deep 
+  in the tails or close to the monomer head groups. Methanol molecules which experience
+  State 3 have by far the smallest local number density which is likely responsible for 
+  their mobility, as suggested by the state's large covariance.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{local_densities.pdf}
+  \caption{We measured the local number density of heavy atoms surrounding solutes in each
+  state. In blue, we plot the local number density experienced by solutes averaged over all
+  frames in which the solute occupied the given state. We broke down this overall average 
+  number density into number densities measured from instances when the state is occupied 
+  for long (orange) versus short(red) dwell time states. We define define `long' dwells times
+  as the 50th percentile of all dwell times in the given state, and short as all others. It
+  is clear that solutes which experience longer dwells times are also surrounded by more 
+  heavy atoms on average.}\label{fig:local_densities}
+  \end{figure}
+
 \end{document}

### 2020-05-22 Ben_Manuscripts/hdphmm/Draft.tex
Updated draft.

@@
   simulations in a cross-linked inverted hexagonal phase lyotropic liquid crystal (LLC)
-  membrane in order to automatically detect a variety of solute dynamical states
-  which can be further explained in terms of solute-membrane interactions.
-
-  We group the states identified by the HDP-AR-HMM into clusters based on multiple metrics
+  membrane in order to automatically detect a variety of solute dynamical states. 
+  %MRS: starts to mix interpretation in with the machine learning too early?  You don't really 
+  explain how the individual states can be explained at this point  
+  %which can be further explained in terms of solute-membrane interactions.
+
+  %MRS: changing to lead with WHY we group them.
+  We can better understand the mechanisms controlling these dynamic states 
+  by grouping the states identified by the HDP-AR-HMM into clusters based on multiple metrics
   aimed at distinguishing solute behavior based on their fluctuations, dwell times
@@
   prevalent clusters in order to relate their parameters to physical interactions between 
-  solutes and the membrane. Along with parameters of individual states, the HDP-AR-HMM 
+  solutes and the membrane.
+
+  Along with parameters of individual states, the HDP-AR-HMM 
   simultaneously infers a transition matrix which allows us to stochastically propagate
@@
 
-  %MRS: we have to decide if ``effective'' is the right word. Alternative is ``promising''.
-  %BJC5: ``promising'' seems safer
   Overall, this work provides a promising way to simultaneously identify transport 
@@
 
-  The ability to efficiently design novel membrane materials for selective separations
-  would be greatly enhanced by easily interpretable methods for connecting microscopic
-  fluctuations with macroscopic observables. If one could apply molecular dynamics 
-  (MD) simulations to explain important experimental metrics such as solute flux and 
-  selectivity in terms of detailed chemically dependent solute motion, then we can more
-  easily bridge the disconnect between theory and application. In many systems, it is 
-  possible to achieve this by calculating diffusion constants. 
   % BJC4: even if we could calculate diffusion constants, wouldn't there still be value 
@@
   % the slopes should be a product of the short time scale motion.
-  Unfortunately, for 
-  systems which exhibit complex short timescale subdiffusive dynamics, one cannot 
-  reliably compute diffusion constants since solute mean square 
-  displacements (MSDs) are non-linear on the timescales accessible to molecular simulation.
-  Therefore, we are in need of a more flexible approach for modeling solute dynamics
-  which makes less assumptions about the solute's short time scale behavior.
+  %MRS: OK, did a pass below, reorganizing it a bit.  See what you think. I think it's OK to talk
+  %about subdiffusion because it's general problem, we aren't making claims about this one.
+
+  The ability to efficiently design novel membrane materials for
+  selective separations would be greatly enhanced by easily
+  interpretable methods for connecting microscopic fluctuations with
+  macroscopic observables. If one can use molecular dynamics (MD)
+  simulations to explain important experimental metrics such as solute
+  flux and selectivity in terms of detailed chemically dependent
+  solute motion, then we can more easily bridge the disconnect between
+  theory and application. In many simple systems, short-time scale
+  dynamics and large scale properties can be connected by the simple
+  the relationship between the mean square displacement (MSD) of the
+  solutes and the macroscopic diffusion constant.  However, for
+  systems which exhibit complex short timescale subdiffusive dynamics,
+  one cannot reliably compute diffusion constants because MSDs are often
+  non-linear on the timescales accessible to molecular
+  simulation. Additionally, direct calculations of diffusion constant
+  may obscure the molecular mechanisms controlling transport,
+  hindering the ability to understand or modulate these mechanisms in new membrane 
+  materials. We are therefore in need of a more flexible approach for modeling solute 
+  dynamics which makes less assumptions about the solute's short time scale behavior.
 
@@
   phases can be cross-linked into mechanically strong membranes capable of highly 
-  selective separations. Inverted hexagonal, H\textsubscript{II}, phase LLC membranes
+  selective separations. Inverted hexagonal phase, or H\textsubscript{II}, LLC membranes
   are characterized by hexagonally packed, uniform-sized and straight pores, an ideal
@@
 
-  In this work we attempt to minimize human effort through a novel application of 
-  the sticky hierarchical Dirichlet process autoregressive hidden Markov model 
+  In this work we attempt 
+  %MRS: 
+  %to minimize human effort 
+  uncover similar physical meaning through a data-driven process. 
+  We utilize the sticky hierarchical Dirichlet process autoregressive hidden Markov model 
   (HDP-AR-HMM), a nonparameteric Bayesian classification technique that allows the user to 
@@
   Given a series of observations and a known number of hidden states, the 
-  Baum-Welch algorithm, an expectation maximization technique, is the most commonly 
+  Baum-Welch algorithm, an expectation maximization technique, is a commonly 
   used way to determine the hidden state sequence and the underlying parameters of
-  a standard HMM.~\cite{baum_maximization_1970} It also possible to achieve the same
+  a standard HMM,~\cite{baum_maximization_1970} though it is also possible to achieve the same
   results using a Bayesian framework.~\cite{scott_bayesian_2002,jasra_markov_2005} 
@@
   % There are pure Bayesian ways to do it. Tried to clarify above.
-  One can place priors on the transition probabilities and parameters of the hidden 
+  % MRS5: there's some implication in the above about what you will use; I tried to make it more general. 
+  One can also place priors on the transition probabilities and parameters of the hidden 
   states' emission distributions in order to iteratively infer their values and to
@@
 
-  The usefulness of the sticky HDP-HMM has been further extended to include 
+  The utility of the sticky HDP-HMM has been further extended to include 
   temporal dependencies common to many real datasets. State dynamics and 
@@
   identification.~\cite{calderon_inferring_2015,hamada_modeling_2016}
-  Not only do we use the HDP-AR-HMM to segment MD time series into distinct
-  dynamical modes, but we cluster and analyze the temporally-correlated 
+  In our approach, we use the HDP-AR-HMM to segment MD time series into distinct
+  dynamical modes, and we cluster and analyze the temporally-correlated 
   parameters of the model in order to learn physical mechanisms and describe
-  solute kinetics. Further, we use the model parameters to generate new 
-  time series trajectories which enables projections of MD simulations on 
-  arbitrary length time scales.
+  solute kinetics. We can use the model parameters determined either before 
+  or after clustering to generate new 
+  time series trajectories which enable projections 
+  %MRS5: tweaking
+  %of MD simulations on
+  of the MD-generated time series to arbitrary length time scales.
 
@@
   We aim to address two primary scientific questions with this work:
-  First, we want to know whether it is possible to use the HDP-AR-HMM to 
+  \begin{enumerate}
+  \item First, we want to know whether it is possible to use the HDP-AR-HMM to 
   help us predict macroscopic transport properties. We use the VAR parameters
@@
   regular diffusive behavior again occurs.
-  Second, we want to know if the HDP-AR-HMM algorithm can help researchers
+  \item Second, we want to know if the HDP-AR-HMM algorithm can help
+  %MRS5: I actually think passive voice works better here, since we want to know if it helps in general.
+  %researchers
   efficiently uncover underlying transport mechanisms which give rise to different 
@@
   solute-membrane interactions.
+  \end{enumerate}
 
@@
   the HDP-AR-HMM and related models.~\cite{fox_bayesian_2010} 
-  %MRS: possibly should give the permanent reference to a shirtsgroup fork?  We can discuss which is likely to be more permenant  
+  %MRS: possibly should give the permanent reference to a shirtsgroup fork?  We can discuss which is likely to be more permanent  
   All other post-simulation trajectory analysis tools are available online at
@@
   these systems are detailed in our previous work.\cite{coscia_chemically_2019}
+  %MRS5: might want to mention above that there was no sign of clustering of solutes (if that is true)
 
@@
   Parrinello-Rahman 
-  %MRS: just wondering, was this semiisotropic, or isotropic?  If isotropic, do we know how different the diagonals of the pressure tensor were (since the system is not totally isotropic)
-  %BJC5: I use semi-isotropic (xy together and z separate)
   barostat~\cite{parrinello_polymorphic_1981} and velocity rescale 
@@
   sensitive to the inputs to the MNIW conjugate priors. The precise boundaries of 
-  the state segments can fluctuate, therefore in states with a low number of 
-  emissions,  the variance in $A$ and $\Sigma$ parameters. In these cases, plateauing
+  the state segments can fluctuate; therefore, in states with a low number of 
+  emissions,  the variance in $A$ and $\Sigma$ parameters. 
+  %MRS5: grammar in previous sentence unclear?  I tried to clean up, but failed.
+  In these cases, plateauing
   of the mean in each dimension tends to be a more reliable indicator of convergence (see 
@@
   It is usually beneficial to employ intelligent state sequence initialization procedures. 
-  Most importantly, states identified by the HDP-AR-HMM are heavily influenced by the 
+  Most importantly, the states identified by the HDP-AR-HMM are heavily influenced by the 
   Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. In 
@@
 
-  We clustered like parameter sets in order to reduce the state space to
+  We clustered states wit like parameter sets in order to reduce the state space to
   a more easily interpretable size. For each solute studied, we identified approximately 
@@
   in finalized parameter sets that are averages of distinct behavior. Since choosing 
-  the number of clusters depends on user-selected criteria, we give an in depth 
+  the number of clusters depends on user-selected criteria, we give an in-depth 
   justification of our approach to choosing the number of clusters in 
@@
     \item For each independent MD trajectory, we generated stochastic trajectory
-    realizations using the finalized parameters of the associated HDP-AR-HMM. This 
+    realizations using the final parameters of the associated HDP-AR-HMM. This 
     results in 24 separate ensembles of trajectories for each solute studied. 
@@
   estimated $D$ from the slope fit between 5 ns and 1000 ns. We used weighted 
+  %MRS5: is 5 ns to low?
   least squares to fit the slope with weights determined by the number of time 
@@
   ensemble of characteristic trajectories. The stochastic trajectories 
-  generated by the parameters of the HDP-AR-HMM (blue) show the same hopping
+  generated by the parameters of the HDP-AR-HMM (blue) show 
+  %MRS: not sure we can say quite the same 
+  %the same 
+  similar hopping
   and trapping behavior exhibited by MD (black).
@@
   Since we can generate trajectories that share the qualitative and quantitative
-  features of our MD simulations, we can now use realizations of the HDP-AR-HMM
+  features of our MD simulations, we can use realizations of the HDP-AR-HMM
   in order to estimate selectivity as described in Section~\ref{method:selectivity}.
@@
 
+  %MRS5: well-written paragraph, tells a convincing story.
   If we can understand the mechanisms that lead to the various observed transport
@@
 
-  \textit{Dynamics of clustered parameter sets}: The clustered parameter sets
-  allow transitions between dynamics exhibited by the same solute from independent 
-  trajectories. This allows us to create hybrid trajectories which draw on all
-  solute behavior.
+  \textit{Dynamics of clustered parameter sets}: The clustered
+  parameter sets allow transitions between dynamics exhibited by the
+  same solute from independent trajectories. This allows us to create
+  hybrid trajectories which draw on dynamics of all the solutes
+  simultaneously.
 
@@
   realizations of our model using the clustered parameter sets. They lack the
-  diversity of behavior which we see in the MD simulation trajectories.
-  They do not show the same range of trapping times and hop lengths. If we use
+  diversity of behavior which we see in the MD simulation trajectories, in particular, 
+  they do not show the same range of trapping times and hop lengths. If we use
   a higher number of clusters, the qualitative match improves, but at the cost
@@
   \end{subfigure}
+  %MRS5: should make it clearer these are from the 10 clusters studied earlier. 
   \caption{(a) Stochastic trajectory realizations generated from our model (blue) based on
@@
   amount of time spent in each varies widely. 
+  %MRS5: maybe explicitly indicate the 5 stattes?  I only see four red bars with appreciable sampling.
   % The solutes spend varying amounts of time in each of these states.
@@
   times. These are fleeting interactions since it is likely a jumping state.
+  %MRS5: not clear what a ``jumping state'' is.
   Methanol molecules in state 5 hydrogen bond almost exclusively to the carboxylate
@@
   \end{subfigure}
+  %MRS5: specifically mention at the beginning which solute.
   \caption{(a) We analyzed hydrogen bond donation to the highlighted oxygen atoms in three 
   regions of the monomer: the carboxylate groups (blue), the ether linkages (green) and the
+  %MRS5: be more clear what ``dominant state'' means in connection with the text.
   tails (red). (b) For each dominant state, we plotted the fraction of the total time in
@@
   clustered states for each solute are inversely related to the solute's MSD. 
+  %MRS5: four subfigures, should all be described in caption
+  %MRS5: not clear what ``largest expected'' means here.
  }\label{fig:summaries}
@@
   simulations. Vector autogregressive models can describe a diverse set of behavior
-  and so the HDP-AR-HMM may be suited to study many types motion, including those not 
+  and so the HDP-AR-HMM may be suited to study many types of motion, including those not 
   characterized by hopping and trapping. The HDP-AR-HMM is a powerful approach for 
   understanding particle motion as well as for generating inexpensive models
+  %MRS5: maybe, `` generating inexpensive models'' -> ``modeling long-time scale trajectories''
  which can give macroscopic insight.
@@
 % LocalWords:  plateaued nclusters leftmargin trans diffusivity sorption alkane
-% LocalWords:  ness substituents
+% LocalWords:  ness substituents desalination fonseca couto welch singhal noe
+% LocalWords:  shirtsgroup superdiffusive diffusivities

### 2020-05-22 Ben_Manuscripts/hdphmm/Draft.tex
added more response.
Added new figures, revisions

@@
   simulations in a cross-linked inverted hexagonal phase lyotropic liquid crystal (LLC)
-  membrane in order to automatically detect a variety of solute dynamical states. 
-  %MRS: starts to mix interpretation in with the machine learning too early?  You don't really 
-  explain how the individual states can be explained at this point  
-  %which can be further explained in terms of solute-membrane interactions.
-
-  %MRS: changing to lead with WHY we group them.
-  We can better understand the mechanisms controlling these dynamic states 
-  by grouping the states identified by the HDP-AR-HMM into clusters based on multiple metrics
+  membrane in order to automatically detect a variety of solute dynamical modes.
+
+  We can better understand the mechanisms controlling these dynamical modes by grouping 
+  the states identified by the HDP-AR-HMM into clusters based on multiple metrics
   aimed at distinguishing solute behavior based on their fluctuations, dwell times
@@
 
-  Along with parameters of individual states, the HDP-AR-HMM 
-  simultaneously infers a transition matrix which allows us to stochastically propagate
-  solute behavior from all of the independent trajectories onto arbitrary length time 
-  scales while still preserving the qualitative behavior characteristic of the MD 
-  trajectories. This affords a direct connection to important macroscopic observables 
-  used to characterize performance like solute flux and selectivity.
+  Along with parameters of individual states, the HDP-AR-HMM simultaneously infers a 
+  transition matrix which allows us to stochastically propagate solute behavior from 
+  all of the independent trajectories onto arbitrary length time scales while still 
+  preserving the qualitative behavior characteristic of the MD trajectories. This 
+  affords a direct connection to important macroscopic observables used to characterize
+  performance like solute flux and selectivity.
 
@@
   %about subdiffusion because it's general problem, we aren't making claims about this one. 
-
-  The ability to efficiently design novel membrane materials for
-  selective separations would be greatly enhanced by easily
-  interpretable methods for connecting microscopic fluctuations with
-  macroscopic observables. If one can use molecular dynamics (MD)
-  simulations to explain important experimental metrics such as solute
-  flux and selectivity in terms of detailed chemically dependent
-  solute motion, then we can more easily bridge the disconnect between
-  theory and application. In many simple systems, short-time scale
-  dynamics and large scale properties can be connected by the simple
-  the relationship between the mean square displacement (MSD) of the
-  solutes and the macroscopic diffusion constant.  However, for
-  systems which exhibit complex short timescale subdiffusive dynamics,
-  one cannot reliably compute diffusion constants because MSDs are often
-  non-linear on the timescales accessible to molecular
-  simulation. Additionally, direct calculations of diffusion constant
-  may obscure the molecular mechanisms controlling transport,
-  hindering the ability to understand or modulate these mechanisms in new membrane 
-  materials. We are therefore in need of a more flexible approach for modeling solute 
-  dynamics which makes less assumptions about the solute's short time scale behavior.
+  %BJC6: looks good!
+
+  The ability to efficiently design novel membrane materials for selective separations 
+  would be greatly enhanced by easily interpretable methods for connecting microscopic
+  fluctuations with macroscopic observables. If one can use molecular dynamics (MD)
+  simulations to explain important experimental metrics such as solute flux and 
+  selectivity in terms of detailed chemically dependent solute motion, then we can 
+  more easily bridge the disconnect between theory and application. In many simple 
+  systems, short-time scale dynamics and large scale properties can be connected by
+  the simple relationship between the mean square displacement (MSD) of the solutes
+  and the macroscopic diffusion constant. However, for systems which exhibit complex 
+  short timescale subdiffusive dynamics, one cannot reliably compute diffusion 
+  constants because MSDs are often non-linear on the timescales accessible to molecular
+  simulation. Additionally, direct calculations of diffusion constant may obscure the
+  molecular mechanisms controlling transport, hindering the ability to understand or 
+  modulate these mechanisms in new membrane materials. We are therefore in need of a 
+  more flexible approach for modeling solute dynamics which makes less assumptions 
+  about the solute's short time scale behavior.
 
@@
 
-  In this work we attempt 
-  %MRS: 
-  %to minimize human effort 
-  uncover similar physical meaning through a data-driven process. 
+  In this work we attempt uncover similar physical meaning through a data-driven process. 
   We utilize the sticky hierarchical Dirichlet process autoregressive hidden Markov model 
@@
   results using a Bayesian framework.~\cite{scott_bayesian_2002,jasra_markov_2005} 
-  %MRS: not entirely clear what purpose of above sentence its - it sort of implied you will use Bayesian framework?
-  % BJC5: Baum welch is most widely used for pure HMM but is an expectation maximization algorithm
-  % There are pure Bayesian ways to do it. Tried to clarify above.
-  % MRS5: there's some implication in the above about what you will use; I tried to make it more general. 
   One can also place priors on the transition probabilities and parameters of the hidden 
@@
 
-  %MRS: define what ``this'' is - important claim, make it clear what it is you are claiming.
   To our knowledge, applying the HDP-AR-HMM in order to gain kinetic and
   mechanistic insight from MD simulation trajectories has not been done
-  before.
-  % this is a novel application and analysis of the sticky HDP-AR-HMM.
-  Typical applications of the HDP-AR-HMM center around determining the 
+  before. Typical applications of the HDP-AR-HMM center around determining the 
   number of states, the state sequence and occasional analysis of the emission 
@@
   solute kinetics. We can use the model parameters determined either before 
-  or after clustering to generate new 
-  time series trajectories which enable projections 
-  %MRS5: tweaking
-  %of MD simulations on
-  of the MD-generated time series to arbitrary length time scales.
-
-  %BJC4: enumerate?
-  %BJC4: might be able to condense this since some of it repeats above.
+  or after clustering to generate new time series trajectories which enable 
+  projections of the MD-generated time series to arbitrary length time scales.
+
   We aim to address two primary scientific questions with this work:
@@
   \item Second, we want to know if the HDP-AR-HMM algorithm can help
-  %MRS5: I actually think passive voice works better here, since we want to know if it helps in general.
-  %researchers
   efficiently uncover underlying transport mechanisms which give rise to different 
@@
   10\% water by weight. Approximately one third of the water molecules 
-  occupy the tail region with the rest near the pore center.%MRS: cite previous paper here on this.
+  occupy the tail region with the rest near the pore center.~\cite{coscia_chemically_2019}
 
   We chose to study a subset of 4 of the fastest moving solutes from our previous
-  work: methanol, acetic acid, urea and ethylene glycol.
-  In addition to exploring membrane structural space the most, these solutes have a
-  relatively diverse set of chemical functionality. For each solute we created a 
-  separate system and to each system we added 6 solutes per pore for a total of 24 solutes. This number 
-  of solutes per pore provides a balance of a low degree of interaction between 
-  solutes and a sufficient amount of data from which to generate statistics on the
-  time scales which we simulate. Further details on the setup and equilibration of
-  these systems are detailed in our previous work.\cite{coscia_chemically_2019}
-  %MRS5: might want to mention above that there was no sign of clustering of solutes (if that is true)
+  work: methanol, acetic acid, urea and ethylene glycol. In addition to exploring 
+  membrane structural space the most, these solutes have a relatively diverse set
+  of chemical functionality. For each solute we created a separate system and to 
+  each system we added 6 solutes per pore for a total of 24 solutes. This number 
+  of solutes per pore provides a sufficient amount of data from which to generate 
+  statistics on the time scales which we simulate and prevents solute clustering
+  facilitating our study of pure solute-membrane interactions. Further details on
+  the setup and equilibration of these systems are detailed in our previous work.~\cite{coscia_chemically_2019}
 
@@
   fs at a pressure of 1 bar and temperature of 300K controlled by the semi-isotropic 
-  Parrinello-Rahman 
-  barostat~\cite{parrinello_polymorphic_1981} and velocity rescale 
+  Parrinello-Rahman barostat~\cite{parrinello_polymorphic_1981} and velocity rescale 
   thermostat~\cite{bussi_canonical_2007} respectively. We recorded configurations every 0.5 ns.
@@
   states for appreciable amounts of time.
-%  We analyze solute motion in terms of their
-%  cylindrical coordinates, $(r, z)$, with the $z$ axis oriented along the membrane 
-%  pores and the radial dimension, $r$, measured from the closest pore center.
 
@@
 
-  %\subsubsection*{Parameterizing the Hidden States}\label{method:var_params}
   \textit{Parameterizing the Hidden States}: We describe the dynamics of each 
@@
 
-%  \subsubsection*{Applying the HDP-AR-HMM to MD Trajectories}
-
   \textit{State sequence and parameter inference}: We inferred the 
@@
   the state segments can fluctuate; therefore, in states with a low number of 
-  emissions,  the variance in $A$ and $\Sigma$ parameters. 
-  %MRS5: grammar in previous sentence unclear?  I tried to clean up, but failed.
-  In these cases, plateauing
-  of the mean in each dimension tends to be a more reliable indicator of convergence (see 
-  Figure~\ref{S-fig:convergence3d} of the Supporting Information).
+  emissions, the variance in $A$ and $\Sigma$ parameters can be high. In these 
+  cases, plateauing of the mean in each dimension tends to be a more reliable 
+  indicator of convergence (see Figure~\ref{S-fig:convergence3d} of the Supporting
+  Information).
 
@@
   procedure.
-  %For example, one can gain a thorough understanding of the dynamics of
-  %different kinds of trapping behavior related to hydrogen bonding and sodium ion association.
-  %MRS: last sentence is a little weird. Audience may be left without knowing how this could be achieved.
 
@@
   the inference component of the HDP-AR-HMM algorithm on this modified trajectory to 
-  infer the clustered state parameters by fixing the clustered state sequence.
+  infer the clustered state parameters by fixing the clustered state sequence. See
+  Section~\ref{S-section:ihmm_procedure} for figures illustrating this process.
 
@@
   \subsection{Predicting Mean Squared Displacement}\label{method:realizations}
-  %BJC4: reworked this section
-  %MRS: should explain why here there are two approaches.
+
   \textit{Generating Stochastic HDP-AR-HMM Trajectory Realizations}: We used two 
@@
 
-  %BJC4: new section below
   \subsection{Predicting Selectivity}\label{method:selectivity}
@@
   %BJC: need to confirm these details
-  For all solutes, we generated 200 ensembles of 24 10 $\mu s$ trajectories and 
-  estimated $D$ from the slope fit between 5 ns and 1000 ns. We used weighted 
-  %MRS5: is 5 ns to low?
+  For all solutes, we generated 200 ensembles of 24 5 $\mu s$ trajectories and 
+  estimated $D$ from the slope fit between 10 ns and 1000 ns. We used weighted 
   least squares to fit the slope with weights determined by the number of time 
@@
   ensemble of characteristic trajectories. The stochastic trajectories 
-  generated by the parameters of the HDP-AR-HMM (blue) show 
-  %MRS: not sure we can say quite the same 
-  %the same 
-  similar hopping
+  generated by the parameters of the HDP-AR-HMM (blue) show similar hopping
   and trapping behavior exhibited by MD (black).
-%  We can use realizations of the HDP-AR-HMM to generate trajectories which 
-%  bear qualitative resemblance to the MD trajectories. 
   }\label{fig:qualitative_unclustered}
@@
   1 described in Section~\ref{method:realizations} of the methods. Our ability
-  to reproduce the MSDs gives us confidence in their long term predictions.
-  %MRS: not match under any circumstance, or without clustering (?  Not clear. 
-  %BJC5: not exactly sure what you're asking here. This section has no clustering 
+  to reproduce the MSDs with stochastic models learned from the trajectories gives us confidence in their long term predictions.
   We underestimate the MSD of urea because of a small number of MD trajectories
@@
   adequately parameterize an HDP-AR-HMM which reproduced the uncharacteristic
-  behavior (see SI).
-%BJC5: TODO.
-There are a couple trajectories I want to show have very high MSDs because all the hops are in one direction along the pore.
-The curves look superdiffusive.
-I think on longer timescales, this wouldn't happen.
-I'll also show the MD MSD curves without the 'outliers' in the SI.
+  behavior (see Section~\ref{S-section:urea_underestimate} of the Supporting Information).
   On long time scales, the model's MSD appear to have a slope similar to the MD 
@@
 
-  %BJC5: need to update legend to say HDP-AR-HMM
+  %BJC6: added. Should I add a figure?
+  A potential shortcoming of the HDP-AR-HMM is its inability to reproduce the 
+  short time scale MSD curves. The MSDs predicted by the model tend to enter
+  a linear regime much more quickly than the MD MSDs (see 
+  Figure~\ref{S-fig:unclustered_msd_shortlag} of the Supporting Information
+  for example). This is not a major concern for predicting macroscopic properties
+  since we are primarily interested in reproducing the MSDs on much longer 
+  timescales.
+  %BJC6: could hypothesize why using previous work as support
+
   \begin{figure}
@@
   \subsection{Using HDP-AR-HMM Parameters to Predict Selectivity}\label{section:macroscopic_properties}
-
-  %MRS: seems odd not at least mention clustering here.
-  %BJC5: I haven't talked about clustering yet. Should this section get moved later? I think it leads into the next section well here.
 
@@
   a higher number of clusters, the qualitative match improves, but at the cost
-  of a larger state space to interpret (see Figure~\ref{S-fig:qualitative_improvement}
+  of a larger state space to interpret (see Section~\ref{S-section:qualitative}
   of the Supporting Information).
@@
   more clusters, at which point the benefits of clustering are lost.
-    %BJC: I don't think the following discussion is necessary anymore.
-%    \item In Figure~\ref{fig:dwell_distributions}, we compare the overall dwell time
-%    distributions generated directly from MD simulations to that generated from 
-%    realizations of the HDP-AR-HMM. 
-%    \item We do this by measuring the time spent in each independent same-state segment.
-%    \item Some of the probability density of short trapping times in the MD simulations 
-%    gets shifted to medium length trapping times in realizations of the HDP-AR-HMM. 
-%    \item In Figure~\ref{fig:dwell_distributions_modT} and~\ref{fig:msd_modT}, we show 
-%    that by modifying the transition matrix to encourage transitions towards states with
-%    shorter dwell times, we can more closely reproduce the dwell time distribution and 
-%    MSD of MD. This is because most solute motion is a consequence of transitions between
-%    trapped states.
 
@@
   \caption{(a) Stochastic trajectory realizations generated from our model (blue) based on
-  the clustered methanol parameters do not qualitatively reproduce the diversity of behavior
-  seen in our MD trajectories. (b) MSD predictions by clustered parameter sets consistently
+  the 10 clustered methanol parameter sets do not qualitatively reproduce the diversity
+  of behavior seen in our MD trajectories. (b) MSD predictions by clustered parameter sets consistently
   under-predict the MD MSD. They appear to do a better job of predicting MSDs as the number
@@
 
-  %BJC5: new
   It is possible that we could improve the MSD predictions generated by the 
@@
   parameters in order to better distinguish states with long dwell times
-  and high variance when clustering.
-%  Since we hypothesized that the lack of short dwell
-%  times is largely responsible for the under-prediction of the MSDs, we could
-%  modify the dwell time clustering procedure in order to better emphasize short
-%  dwells times.
-  However, we did not pursue this too far in order to avoid over-fitting the data.
-  %BJC5: maybe an SI figure showing some different approaches
+  and high variance when clustering. However, we did not pursue this too 
+  far in order to avoid over-fitting the data.
 
@@
 
-  %Although a majority of the solutes
-  %visit these 5 dominant states the amount of time spent in each varies widely.
-
   \begin{figure}
@@
   \caption{5 out of the 10 clustered states are visited by 15 or more of the solute
-  trajectories. Although a majority of the solutes visit these 5 dominant states, the
-  amount of time spent in each varies widely. 
+  trajectories (States 1--5). Although a majority of the solutes visit these 5 
+  dominant states, the amount of time spent in each varies widely. For example, methanol
+  does not spend a significant amount of time in State 3 because, as discussed later, it 
+  is a short-lived state. We still consider State 3 as a dominant state because it
+  is may be a significant contributer to solute MSD.
   %MRS5: maybe explicitly indicate the 5 stattes?  I only see four red bars with appreciable sampling.
   % The solutes spend varying amounts of time in each of these states.
+  %BJC6: I'm focusing on the blue bars. It's a hopping state so not much time is spent there,
+  % but most of the solutes still show that behavior. Added a couple sentences to clarify
   }
@@
      the pore center and tail ends. Evidence from Figure~\ref{fig:clustered_traj_MET} 
-     suggests that this state is common both close to the pore center and in the tail
-     and region.
-     % MRS: ``tail and pore region'' sounds the same as ``everywhere''.
-     % BJC5: That's kind of what I mean. Behavior is similar near pore center and far
-     % from pore center. Half happen at pore, half happen in tails, average r is 1.5 nm
+     suggests that this state occurs essentially evenly across possible radial
+     distances from the pore center.
      \item This state's radial mean of 2.4 nm implies that it occurs exclusively in the
@@
   bond and sodium association lifetimes which is consistent with its short dwell
-  times. These are fleeting interactions since it is likely a jumping state.
+  times. These are fleeting interactions since it is likely a high variance 
+  transitory state.
   %MRS5: not clear what a ``jumping state'' is.
+  %BJC6: tried to be more precise. changed to 'high variance transitory state'
   Methanol molecules in state 5 hydrogen bond almost exclusively to the carboxylate
@@
   %MRS5: specifically mention at the beginning which solute.
-  \caption{(a) We analyzed hydrogen bond donation to the highlighted oxygen atoms in three 
-  regions of the monomer: the carboxylate groups (blue), the ether linkages (green) and the
-  %MRS5: be more clear what ``dominant state'' means in connection with the text.
-  tails (red). (b) For each dominant state, we plotted the fraction of the total time in
-  that state spent hydrogen bonding to various regions of the monomer, color coded to match (a).
+  \caption{(a) We analyzed hydrogen bonds donated by methanol to the highlighted oxygen
+  atoms in three regions of the monomer: the carboxylate groups (blue), the ether linkages
+  (green) and the tails (red). (b) For each dominant state (States 1--5 described in 
+  Figure~\ref{fig:prevalence}, we plotted the fraction of the total time in that state 
+  spent hydrogen bonding to various regions of the monomer, color coded to match (a).
   (c) For each type of hydrogen bond in each dominant state, we calculated the 95th percentile
@@
   time it occupies any of the dominant state.
-  %Relative to hydrogen bonding, it is a relatively infrequent interaction
-  %for methanol molecules, but the 
   }
@@
   their time close to the pore center. Only methanol has a significant density
-  far from the pore center. (c) The largest expected dwell time among the dominant 
-  clustered states for each solute are inversely related to the solute's MSD. 
-  %MRS5: four subfigures, should all be described in caption
+  far from the pore center. (c) The largest expected value (see~\ref{eqn:dwell_times})
+  of dwell times among the dominant clustered states for each solute are inversely
+  related to the solute's MSD. 
   %MRS5: not clear what ``largest expected'' means here.
+  %BJC6: modified to 'expected value' and referenced equation   
+  (d) The expected dwell time of solutes increases 
+  in states with high local number density of surrounding heavy atoms.
   }\label{fig:summaries}
@@
   recognize the generality of this analysis, especially in the context of molecular
-  simulations. Vector autogregressive models can describe a diverse set of behavior
+  simulations. Vector autoregressive models can describe a diverse set of behavior
   and so the HDP-AR-HMM may be suited to study many types of motion, including those not 
   characterized by hopping and trapping. The HDP-AR-HMM is a powerful approach for 
-  understanding particle motion as well as for generating inexpensive models
-  %MRS5: maybe, `` generating inexpensive models'' -> ``modeling long-time scale trajectories''
+  understanding particle motion as well as for modeling long time scale trajectories
   which can give macroscopic insight.

### 2020-05-25 Ben_Manuscripts/hdphmm/Supporting_Information.tex

@@
 \documentclass{article}
+
+\usepackage{tocloft}
+
+\renewcommand\cftsecfont{\normalfont}
+\renewcommand\cftsecpagefont{\normalfont}
+\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}}
+\renewcommand\cftsecdotsep{\cftdot}
+\renewcommand\cftsubsecdotsep{\cftdot}
+\cftsetindents{section}{0em}{3em}
+%\cftsetindents{subsection}{1em}{3em}
 
@@
   \maketitle
+  \tableofcontents
 
@@
 
-  The state sequence appears to converge within 500--1000 IHMM iterations. Step 1
-  in the procedure from the previous section is the only time the state sequence 
-  is determined. We ran 2000 iterations of the IHMM algorithm in order to arrive
-  at a finalized state sequence. Stabilization of the VAR parameters indicates 
+  The state sequence appears to converge within 500--1000 IHMM iterations. To
+  be sure, we ran 2000 iterations of the IHMM algorithm in order to arrive at a 
+  finalized state sequence. Stabilization of the VAR parameters indicates 
   that the state sequence has converged. In Figure~\ref{fig:convergence3d}, we plot
-  the diagonal entries of 3 different $A$ and $\Sigma$ matrices as well as the 
-  entries of the mean vector $\mathbf{c}$, fit to a single 3D methanol trajectory.
-  States with a relatively small number of observations are more highly influenced 
-  by the boundaries of the state segments and generally lead to much higher 
-  variance of the $A$ and $\Sigma$ parameters. In these cases, the mean is
-  a more reliable indicator of convergence since stabilized means imply that the
-  fluctuations assigned to each state come from motion about a static location.
+  the diagonal entries of the $A$ and $\Sigma$ matrices as well as the entries of
+  the mean vector $\mathbf{c}$, for three different states identified in a 3D 
+  methanol trajectory. States with a relatively small number of observations are
+  more highly influenced by the boundaries of the state segments and generally 
+  lead to much higher variance of the $A$ and $\Sigma$ parameters. In these cases,
+  the mean is a more reliable indicator of convergence since stabilized means 
+  imply that the fluctuations assigned to each state come from motion about a 
+  static location.
 
@@
   \caption{Given a sufficient number of observations for a given mode, the VAR parameters
-  appear to converge within 500 -- 1000 iterations. States with too few observations
-  are more highly influenced by the boundaries of the state segments and generally
+  appear to converge within 500 -- 1000 iterations. States with fewer observations
+  are more highly influenced by the boundaries of the state segments which can
   lead to much higher fluctuations in the VAR parameters.}\label{fig:convergence3d}
@@
 
-  \clearpage
-
-  When we fix the state sequence in subsequent steps of the procedure, parameter 
-  estimates converge within only a few steps. In Figure~\ref{fig:fixed_state_convergence}, we 
-  plot the entries of $A$ and $\Sigma$ as a function of IHMM iteration. Some states
-  are sampled far more frequently than others. High sampling frequently results in
-  higher certainty converged parameter estimates. Due to fast convergence, we only
-  run 100 iterations of the inference behavior when the state sequence is fixed.
+  When we fix the state sequence during the steps of the procedure following the 
+  initial state sequence determination, the parameter estimates converge within 
+  only a few steps. In Figure~\ref{fig:fixed_state_convergence}, we plot the 
+  entries of $A$ and $\Sigma$ as a function of IHMM iteration. Some states are 
+  sampled far more frequently than others. High sampling frequently results in 
+  higher certainty converged parameter estimates. Due to fast convergence, we 
+  only ran 100 iterations of the inference behavior when the state sequence is fixed.
 
@@
 
-  \section{Demonstration of IHMM Parameterization Procedure}\label{section:ihmm_procedure}
+  \section{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
 
-  Parameterization of trajectories by the IHMM is a multi-stepped procedure. In the steps and
-  figures that follow, we graphically illustrate the procedure which is described in detail 
-  in Section~\ref{M-method:IHMM} of the main text.
-
-  \begin{enumerate}
-  	\item Parameterize in $x$, $y$, $z$ coordinates with $x$, $y$ coordinates relative to the nearest
-  	pore center (see Figure~\ref{fig:xyz_hmm}). 		
-  	\item Cluster the VAR parameters from the states found in all 24 trajectories (See 
-  	Section~\ref{method:clustering} of the main text). Reassign the state sequence so that segments
-  	which belong to the same cluster are labeled the same across all solute trajectories.
-  	\item Zero the trajectories. First, zero out the $y$ dimension by rotating each segment of 
-  	the trajectory, as partitioned before clustering, about the $z$ axis, in order to align the 
-  	mean $xy$ vector with the $x$ axis (see Figure~\ref{fig:y_zeroed}). Then, subtract the mean in
-  	$x$ and $z$ (Figure~\ref{fig:xyz_zeroed}.
-  	\item Fix clustered state sequence and infer parameters of each state, assuming a mean of zero
-  	for all states (see Figure~\ref{fig:zeroed_clustered_hmm}). 
-  \end{enumerate}
-
-  \begin{figure}
-    \centering
-	\begin{subfigure}{0.6\textwidth}
-	\includegraphics[width=\textwidth]{xyz_hmm.pdf}
-		\caption{}\label{fig:xyz_hmm}
-	\end{subfigure}  
-		\begin{subfigure}{0.6\textwidth}
-		\includegraphics[width=\textwidth]{y_zeroed.pdf}
-		\caption{}\label{fig:y_zeroed}
-	\end{subfigure}  	
-	\begin{subfigure}{0.6\textwidth}
-		\includegraphics[width=\textwidth]{xyz_zeroed.pdf}
-		\caption{}\label{fig:xyz_zeroed}
-	\end{subfigure}  		
-	\begin{subfigure}{0.6\textwidth}
-		\includegraphics[width=\textwidth]{zeroed_clustered_hmm.pdf}
-		\caption{}\label{fig:zeroed_clustered_hmm}
-	\end{subfigure}  
-	\caption{IHMM parameterization is a multi-step procedure. In the above plots, distinct colors
-	correspond to distinct state behavior. (a) First we parameterize the trajectories in terms of
-	the $x$, $y$, $z$ solute center-of-mass coordinates with the $x$ and $y$ coordinates relative
-	to the nearest pore center (b) Next, we convert the $x$ and $y$ 	
-	coordinates to radial coordinates, $r$, then fix the state sequence and use the inference 
-	component of the IHMM in order to estimate the parameters in terms of $r$ and $z$. Note that
-	the segment colors in (b) are the same as (a) because we fixed the state sequence.
-	(c) After clustering the VAR parameters and reassigning the state sequence so that segments 
-	which belong to the same cluster are labeled the same across all solute trajectories, we subtract
-	the mean of each segment, obtained before clustering, in order to zero out the
-  	trajectory, and then fix the clustered state sequence to infer the parameters of each clustered 
-  	state, assuming a mean of zero for all states. Note that the colors are no longer aligned with 
-  	figures (a) and (b) because the states are relabeled in terms of their clusters. There are
-  	also less states in this single trajectory.
-	}\label{fig:hmm_demo}
-  \end{figure}
-
-  \newpage
-
-  \section{Tips for Reliable State Sequence Identification}\label{section:fitting_tips}
+  The IHMM is quite powerful on its own, but requires some critical thinking by
+  the user in order to ensure maximum effectiveness. One can obtain 
+  the best results with some simple checks and, where necessary, improved 
+  state sequence initialization.
 
@@
   results to determine whether further adjustments to the prior might be needed.
-%  In Figure TBD, we show the result of a parameterization where the prior
-%  parameters of $c$ were poorly chosen. %TODO
 
@@
 
-  \pagebreak
+  \textit{Seeding the initial state sequence}: We always initialize the prior on
+  $\mathbf{c}$ as described above but in some 
+  particularly tricky cases, the initial state sequence estimate is so poor that
+  qualitative trajectory realizations and MSD predictions are irreconcilable with
+  MD. A simple way to identify bad parameterizations is to check whether the MD 
+  MSD of individual trajectories can be reasonably reproduced by realizations of
+  the HDP-AR-HMM fit to the same trajectory. In Figure~\ref{fig:msd_overestimate},
+  the MSD predicted by the HDP-AR-HMM dwarfs that calculated from MD, due to 
+  rapid switching between states in the final state sequence.
 
-  The IHMM is quite powerful on its own, but requires some critical thinking by
-  the user in order to ensure maximum effectiveness. One can obtain 
-  the best results with some simple checks and, where necessary, improved 
-  state sequence initialization.
-
-  The best way to ensure reliable MSD predictions is to ensure proper reproduction
-  of the individual MD MSDs by realizations of the IHMM. Over-predictions and 
-  under-predictions are usually the result of a poorly identified state sequence. (see
-  Figure TBD for example)
+  We can improve the final state sequence estimate by seeding the initial state 
+  sequence with a guess made by applying the HDP-AR-HMM to smaller segments of the 
+  trajectory. In Figure~\ref{fig:seed_sequence}, we illustrate this process. In
+  Figure~\ref{fig:msd_improvement}, the MSD predicted by the HDP-AR-HMM is
+  much more consistent with MD after applying this approach.
 
@@
   under-prediction of the MSD, usually due to poor initialization of the state
-  sequence. In (b), state transitions are too frequent and lead to an
-  overprediction of the MD MSD. (c) We can greatly improve MSD predictions by
-  giving the IHMM a good guess at the initial state sequence. (d) A better
-  initial state segmentation via seeding, gives more reasonable estimates
-  of the final state sequence.}\label{fig:improvement_state_sequence}
+  sequence. In (b), state transitions are too frequent, particularly between 
+  the light blue and light green states, and ultimately causes an over-prediction
+  of the MD MSD. (c) We can greatly improve MSD predictions by giving the HDP-AR-HMM a good
+  guess at the initial state sequence. (d) A better initial state segmentation
+  via seeding, gives more reasonable estimates of the final state sequence
+  as illustrated in Figure~\ref{fig:seed_sequence}.}\label{fig:improvement_state_sequence}
   \end{figure}
-
-  There are two primary approaches we have implemented in order to improve the final 
-  state sequence predictions. Both attempt to aid the initial state assignments 
-  algorithmically. First, we always initialize the prior on $\mathbf{c}$ in 
-  Equation~\ref{M-eqn:var} of the main text as described in 
-  Section~\ref{section:prior_guesses}. In particularly tricky cases, the initial
-  state sequence estimate is so poor that qualitative trajectory realizations
-  and MSD predictions are irreconcilable with MD. In our second approach, we can
-  seed the initial state sequence with a guess made by applying the IHMM to 
-  smaller segments of the trajectory.
 
@@
   \includegraphics[width=\textwidth]{seed_ACH21_full.pdf}
-  \caption{Initial state sequence seeded with states found in (a)--(d)}\label{fig:full}
+  \caption{Final state sequence seeded with states found in (a)--(d)}\label{fig:full}
   \end{subfigure}
-  \caption{In (a--d), we show the state sequence resulting from 5 iterations
-  of the IHMM on each of the four quarters of the center-of-mass trajectory in
-  (e) after splitting it into 4 separate segments. We use the concatenation 
-  of the four state sequences as the initial sequence for the IHMM run on the 
-  fully trajectory in (e).
+  \caption{In (a--d), we show the state sequences which result from 5 iterations
+  of the HDP-AR-HMM on each of the four quarters of the center-of-mass trajectory
+  in (e). We use the concatenation of the four state sequences as the initial 
+  sequence for the HDP-AR-HMM inference run on the fully trajectory in (e).
   }\label{fig:seed_sequence}
@@
 
-  % BJC: will show Gaussian mixture model which has a cluster engulfing another cluster, so
-  % it's tails are on both sides of the center cluster.
-
   \begin{figure}[h]
@@
   \includegraphics[width=\textwidth]{bayesian_A.pdf}
-  \caption{Bayesian Gaussian mixture model}\label{fig:bayesian_A}
+  \caption{Dirichlet process Gaussian mixture model}\label{fig:bayesian_A}
   \end{subfigure}
@@
   \end{subfigure}
-  \caption{To reduce the state space, we prefer agglomerative clustering over Bayesian
-  Gaussian mixture modeling. In the plots above we show the results of clustering the
+  \caption{To reduce the state space, we prefer agglomerative clustering over non-parametric
+  Dirichlet process Gaussian mixture modeling. In the plots above we show the results of clustering the
   diagonal entries of the autoregressive coefficient matrices, $A$, of methanol. (a) 
-  Bayesian Gaussian mixture models tend to delocalize the clusters in parameter space
+  Dirichlet process Gaussian mixture models tend to delocalize the clusters in parameter space
   since the Gaussians can overlap. Agglomerative clustering prevents overlap of 
@@
 
-%  \subsection{Clustering on the self-transition probabilities}\label{section:selfT_cluster}
-%  
-%  To cluster on $T_{ii}$, we first cast it in terms of the expected dwell times. The expected 
-%  value of the number of sequential self-transitions is simply $\frac{1}{1 - T_{ii}}$. This 
-%  relationship correctly implies that dwell times approach infinity as $T_{ii}$ approaches 1. 
-%  There we found the most success with agglomerative clustering by linearizing this 
-%  relationship and clustering on $-log(1 - T_{ii})$.
-
   \subsection{Choosing Linkage Criteria and the Number of Clusters}\label{section:nclusters}
@@
   In this section, we determine the optimal linkage criteria and number of clusters
-  for studying methanol's parameters. We applied the same workflow to make analogous
-  decisions for ethylene glycol, urea and acetic acid. In all cases, we found that
-  the `ward' linkage criteria resulted in the most useful clustering. We chose to 
-  use x number of clusters for each solute, the minimum number of clusters, by our
+  for studying methanol's parameters. We applied the same workflow in order to make
+  analogous decisions for ethylene glycol, urea and acetic acid. In all cases, we 
+  found that the `ward' linkage criteria resulted in the most useful clustering. 
+  We chose to use 10 clusters for each solute, the minimum number of clusters, by our
   analysis, needed to adequately distinguish state dynamics.
@@
   total number of clusters. In Figure~\ref{fig:linkages}, we show the result of clustering
-  with each type of linkage criteria available with the 
+  with each type of linkage criteria available with the \\
   \texttt{sklearn.cluster.AgglomerativeClustering} class of the \texttt{scikit-learn} 
@@
   A Silhouette score of 1 indicates the best clustering possible, values near
-  0 indicate overlapping clusters, and negative values indicate samples belong to
+  0 indicate overlapping clusters, and negative values indicate that samples belong to
   the wrong clusters. For the methanol parameters, the Silhouette score drops off
@@
   \begin{subfigure}{0.9\textwidth}
-  \includegraphics[width=1\textwidth]{clustered_traj_MET_ward_12.pdf}
-  \caption{12 total clusters}\label{fig:12cluster_state_sequence}
-  \end{subfigure}
-  \begin{subfigure}{0.9\textwidth}
-  \includegraphics[width=1\textwidth]{clustered_traj_MET_ward_20.pdf}
-  \caption{20 total clusters}\label{fig:20cluster_state_sequence}
+  \includegraphics[width=1\textwidth]{clustered_traj_MET_ward_10_nolabel.pdf}
+  \caption{10 total clusters}\label{fig:20cluster_state_sequence}
   \end{subfigure}
@@
   not see adequate distinction between clusters until we group the parameters
-  from the 24 trajectories into 20 total clusters. When we use 12 total clusters,
-  the distinction appears acceptable except that the segment from ~50--550 ns
-  and from 1200--1500 ns (both colored orange) are clustered together. The radial
-  means of these two segments correspond to two very different morphological
-  regions of the membrane.}\label{fig:clustered_state_sequences}
+  from the 24 trajectories into at least 10 total clusters.}\label{fig:clustered_state_sequences}
   \end{figure}
+
+  \section{Obtaining clustered state parameters}\label{section:ihmm_procedure}
+
+  Parameterization the clustered states with the HDP-AR-HMM is a multi-stepped procedure. 
+  In the steps and figures that follow, we graphically illustrate the procedure which is
+  described with additional detail in Section~\ref{M-method:clustering} of the main text.
+
+  \begin{enumerate}
+  	\item Parameterize in $x$, $y$, $z$ coordinates with $x$, $y$ coordinates relative to the nearest
+  	pore center (see Figure~\ref{fig:xyz_hmm}). 		
+  	\item Cluster the VAR parameters from the states found in all 24 trajectories (See 
+  	Section~\ref{M-method:clustering} of the main text). Reassign the state sequence so that segments
+  	which belong to the same cluster are labeled the same across all solute trajectories.
+  	\item Zero the trajectories. First, zero out the $y$ dimension by rotating each segment of 
+  	the trajectory, as partitioned before clustering, about the $z$ axis, in order to align the 
+  	mean $xy$ vector with the $x$ axis (see Figure~\ref{fig:y_zeroed}). Then, subtract the mean in
+  	$x$ and $z$ (Figure~\ref{fig:xyz_zeroed}).
+  	\item Fix clustered state sequence and infer parameters of each state, assuming a mean of zero
+  	for all states (see Figure~\ref{fig:zeroed_clustered_hmm}). 
+  \end{enumerate}
 
@@
     \centering
-  \includegraphics[width=0.7\textwidth]{nclusters_msd_MET_ward.pdf}
-  \caption{The total MSD predicted by stochastic realizations of the clustered
-  model is relatively insensitive to the total number of clusters. All
-  predictions are less than the predictions of MD and the unclustered trajectories.
-  This behavior is expected due to underestimation of the short dwell time 
-  densities as described in Section~\ref{M-section:unclustered_MSD_prediction}
-  of the main text.}\label{fig:MET_nclusters} 
+	\begin{subfigure}{0.6\textwidth}
+	\includegraphics[width=\textwidth]{xyz_hmm.pdf}
+		\caption{}\label{fig:xyz_hmm}
+	\end{subfigure}  
+		\begin{subfigure}{0.6\textwidth}
+		\includegraphics[width=\textwidth]{y_zeroed.pdf}
+		\caption{}\label{fig:y_zeroed}
+	\end{subfigure}  	
+	\begin{subfigure}{0.6\textwidth}
+		\includegraphics[width=\textwidth]{xyz_zeroed.pdf}
+		\caption{}\label{fig:xyz_zeroed}
+	\end{subfigure}  		
+	\begin{subfigure}{0.6\textwidth}
+		\includegraphics[width=\textwidth]{zeroed_clustered_hmm.pdf}
+		\caption{}\label{fig:zeroed_clustered_hmm}
+	\end{subfigure}  
+	\caption{In the above plots, distinct colors correspond to distinct state behavior. 
+	(a) First we parameterize the trajectories in terms of the $x$, $y$, $z$ solute 
+	center-of-mass coordinates with the $x$ and $y$ coordinates relative to the nearest 
+	pore center. The parameters of these states are used to predict the unclustered MSDs
+	according to method 1 described in Section~\ref{M-method:realizations} of the main
+	text. (b) Next, we zeroed out the $y$ dimension by rotating each segment of the 
+	trajectory, as partitioned before clustering, about the $z$ axis, in order to align the 
+  	mean $xy$ vector with the $x$ axis. (c) We then subtracted the $x$ and $y$ means of
+  	each segment in order to fully zero the trajectory. (d) Finally, we applied the 
+  	inference component of the HDP-AR-HMM in order to infer the parameters of the 
+  	clustered states.
+	}\label{fig:hmm_demo}
   \end{figure}
 
-  This clustering analysis will be finished after some mechanistic studies. It is
-  clear that we will need some understanding of mechanisms in order to 
-  arrive at a cluster recommendation.
+  \newpage
 
-%  \begin{figure}[h]
-%  \centering
-%  \begin{subfigure}{0.475\textwidth}
-%  \includegraphics[width=\textwidth]{nclusters_msd_MET_ward.pdf}
-%  \caption{ward}\label{fig:nclusters_msd_MET_ward}
-%  \end{subfigure}
-%  \begin{subfigure}{0.475\textwidth}
-%  \includegraphics[width=\textwidth]{nclusters_msd_MET_complete.pdf}
-%  \caption{complete}\label{fig:nclusters_msd_MET_complete}
-%  \end{subfigure}
-%  \begin{subfigure}{0.475\textwidth}
-%  \includegraphics[width=\textwidth]{nclusters_msd_MET_average.pdf}
-%  \caption{average}\label{fig:nclusters_msd_MET_average}
-%  \end{subfigure}
-%  \begin{subfigure}{0.475\textwidth}
-%  \includegraphics[width=\textwidth]{nclusters_msd_MET_single.pdf}
-%  \caption{single}\label{fig:nclusters_msd_MET_single}
-%  \end{subfigure} 
-%  \caption{}\label{fig:MET_nclusters} 
-%  \end{figure}
+  \section{Cause of underestimate of urea's MD MSD}\label{section:urea_underestimate}
 
-  \section{Deviations of the IHMM from Molecular Motion}\label{section:shorttimes_msd}
+  Realizations of the HDP-AR-HMM underestimate the MD MSD of urea due to MD
+  trajectories with axial motion correlation that is likely uncharacteristic and
+  unable to be captured by ensembles of stochastic HDP-AR-HMM realizations. One
+  such trajectory is plotted in Figure~\ref{fig:urea_underestimate}. Axial hops 
+  appear positively correlated, jumping consistently in the negative $z$ direction, 
+  leading to a high MSD. The parabolic trajectory of the MD MSD curve implies
+  underlying superdiffusion which would require some kind of facilitating
+  driving force. It is likely that running the trajectory longer would reduce
+  the slope of the MSD curve, making it more consistent with the HDP-AR-HMM 
+  prediction.
 
-   At extremely short time lags, the MSD is generally over-predicted by the IHMM
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.35\textwidth}
+  \includegraphics[width=\textwidth]{underestimate_URE_13.pdf}
+  \caption{}\label{fig:underestimate_msd}
+  \end{subfigure}
+  \begin{subfigure}{0.63\textwidth}
+  \includegraphics[width=\textwidth]{state_sequence_before_URE_13.pdf}
+  \caption{}\label{fig:underestimate_traj}
+  \end{subfigure}
+  \caption{(a) The HDP-AR-HMM under-predicts the MD MSD of urea when fit
+  to the trajectory in (b) because axial hops are highly correlated, 
+  behavior our model is unable to reproduce.}\label{fig:urea_underestimate}
+  \end{figure}
+
+  \section{Influence of number of clusters on qualitative hybrid trajectories}\label{section:qualitative}
+
+  \begin{figure}[h]
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{qualitative_clustered_MET_20.pdf}
+  \caption{20 clusters}\label{fig:qualitative_20}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+  \includegraphics[width=\textwidth]{qualitative_clustered_MET_30.pdf}
+  \caption{30 clusters}\label{fig:qualitative_30}
+  \end{subfigure}
+  \caption{The quality of hybrid trajectories resulting from clustered parameters
+  sets qualitatively improves as the number of clusters is increased. This comes 
+  at the cost of a larger state space to interpret.}\label{fig:qualitative_improvement}
+  \end{figure}
+
+  \section{Deviations of the HDP-AR-HMM from Molecular Motion}\label{section:shorttimes_msd}
+
+  At extremely short time lags, the MSD is generally over-predicted by the HDP-AR-HMM
   (see Figure~\ref{fig:unclustered_msd_shortlag}) because the VAR(1) model assumes
@@
   modeled by more general L\'evy stable noise. The first time lag of the MSD is
-  equivalent to the variance of all observed fluctuations (first-order difference). 
-  The IHMM simulation appears to over-estimate the variance because the actual 
+  equivalent to the variance of all observed fluctuations. 
+  The HDP-AR-HMM simulation appears to over-estimate the variance because the actual 
   distribution of solute fluctuations has heavy tails with a smaller variance (Figure~\ref{fig:emission_widths}).
@@
   interestingly, in Figure ~\ref{fig:state_emission_widths}, we show that the 
-  emission distribution of a single state picked out by the IHMM is fit better by
-  a more general L\'evy distribution while the emissions from IHMM realizations are
-  Gaussian, as expected. An improvement to the IHMM that may allow dynamics more 
+  emission distribution of a single state picked out by the HDP-AR-HMM is fit better by
+  a more general L\'evy distribution while the emissions from HDP-AR-HMM realizations are
+  Gaussian, as expected. An improvement to the HDP-AR-HMM that may allow dynamics more 
   faithful to MD would use an autoregressive model with L\'evy stable noise. However,
@@
 
-  \begin{figure}
+  \begin{figure}[h]
   \centering
@@
   \end{subfigure}
-  \caption{(a) At short time lags, the MD MSD (black) and the IHMM MSD (orange)
+  \caption{(a) At short time lags, the MD MSD (black) and the HDP-AR-HMM MSD (orange)
   differ significantly in their shape and curvature. (b) While the 
   fluctuations in $z$ of both distributions are heavy-tailed, fitting well to zero-centered
-  symmetric L\'evy stable distributions with stability parameters, $\alpha$, the IHMM has
+  symmetric L\'evy stable distributions with stability parameters, $\alpha$, the HDP-AR-HMM has
   a wider variance. (c) The distribution of fluctuations in a chosen state frequently
-  visited by methanol is heavy tailed, but the IHMM is constrained to produce fluctuations
+  visited by methanol is heavy tailed, but the HDP-AR-HMM is constrained to produce fluctuations
   from a multivariate normal distribution ($\alpha$=2 in each dimension).
@@
   Also apparent from Figure~\ref{fig:unclustered_msd_shortlag} is that the 
-  curvature of the MD MSD is far more gradual than that generated by the IHMM.
+  curvature of the MD MSD is far more gradual than that generated by the HDP-AR-HMM.
   This is because the VAR(1) model is only correlated to its previous fluctuation
@@
 
-  \section{Influence of number of clusters on qualitative hybrid trajectories}
+%  \section{MSDs predicted from clustered parameter sets}\label{section:clustered_msds}  
+%  
+%  \begin{figure}[h]
+%  \centering
+%  \includegraphics[width=0.7\textwidth]{nclusters_msd_MET_ward.pdf}
+%  \caption{The total MSD predicted by stochastic realizations of the clustered
+%  model is relatively insensitive to the total number of clusters. All
+%  predictions are less than the predictions of MD and the unclustered trajectories.
+%  This behavior is expected due to underestimation of the short dwell time 
+%  densities as described in Section~\ref{M-section:unclustered_MSD_prediction}
+%  of the main text.}\label{fig:MET_nclusters} 
+%  \end{figure}
 
-  \begin{figure}
-  \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\textwidth]{qualitative_clustered_MET_20.pdf}
-  \caption{20 clusters}\label{fig:qualitative_20}
-  \end{subfigure}
-  \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\textwidth]{qualitative_clustered_MET_30.pdf}
-  \caption{30 clusters}\label{fig:qualitative_30}
-  \end{subfigure}
-  \caption{The quality of hybrid trajectories resulting from clustered parameters
-  sets qualitatively improves as the number of clusters is increased. This comes 
-  at the cost of a larger state space to interpret.}\label{fig:qualitative_improvement}
-  \end{figure}
-
-  \section{Clustered Parameters}\label{section:clustered_parmeters}
+  \section{Relating clustered parameters to mechanisms}\label{section:clustered_parmeters}
 
@@
   radial mean of state 3 is 1.4 nm from the pore center. However, inspection of 
-  Figure~\ref{fig:clustered_traj_MET} suggests that this type of behavior actually
+  Figure~\ref{M-fig:clustered_traj_MET} of the main text suggests that this type of behavior actually
   occurs radially throughout the pore. There are instances of state 3 less than 1 nm
@@
   dwell times and state 3 has the shortest dwell times while the rest have intermediate
-  dwell times. This is somewhat supported by inspection of Figure~\ref{fig:clustered_traj_MET},
-  however. The expected dwell times of the clusters incorporate all 24 trajectories.
-
-  % BJC4: Not sure if this is useful.
-  % MRS: it does give a good summary. But you should make it clear how you selected these 5.
-  % MRS: it's implied in one of the figures, but should be stated explicitly
-%  By examining the parameters, it is now easier to describe the state behavior.
-%  \begin{enumerate}[label={State \theenumi :}, leftmargin=3.5\parindent]
-%     \item This state has intermediate dwell times with high past-hop dependence.
-%     The radial mean and evidence from Figure~\ref{fig:clustered_traj_MET} suggests
-%     %MRS: ``tail and pore region'' sounds the same as ``everywhere''.
-%     that this state is common in the tail and pore region.
-%     \item This state seems to occur exclusively in the tail region based on its radial
-%     mean. Its fluctuations are small and there is little past hop dependence
-%     \item This is likely a hopping state that strongly contribute to the solute's MSD. 
-%     It is short lived and takes very large hops. This type of behavior is exhibited 
-%     %MRS: ``near and far'' also sounds like everywhere 
-%     near and far from the pore center as discussed earlier.
-%     \item This is a trapping state with a strong dependence on its previous fluctuation.
-%     Evidence from Figure~\ref{fig:clustered_traj_MET} and a radial mean of 1.8 suggest
-%     that it tends to occur at intermediate distances from the pore center.
-%     \item This is an intermediate-length trapping state that occurs close to the pore
-%     center. It's fluctuations are tight and relatively independent of its previous 
-%     fluctuation.
-%  \end{enumerate}
+  dwell times. This is somewhat supported by inspection of Figure~\ref{M-fig:clustered_traj_MET},
+  however, the expected dwell times of the clusters incorporate all 24 trajectories.
 

### 2020-05-26 Ben_Manuscripts/hdphmm/Draft.tex
Incorporate Chris' suggestions

@@
 \author{Christopher P. Calderon}
-\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
+\affiliation{Ursa Analytics, Inc., Denver, CO 80212, USA} %CPC:  > 90% of my time spent officially under Ursa 
+\alsoaffiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
 \author{Michael R. Shirts}
@@
   predicting bulk properties characteristic of much longer time scales. In this work 
-  we apply the sticky hierarchical Dirichlet process autoregressive hidden Markov model
-  (HPD-AR-HMM) to solute center-of-mass trajectories generated from long molecular dynamics (MD)
+  we apply nonparametric Bayesian time series analysis, more specifically the sticky 
+  hierarchical Dirichlet process autoregressive hidden Markov model
+  (HDP-AR-HMM) to solute center-of-mass trajectories generated from long molecular dynamics (MD)
   simulations in a cross-linked inverted hexagonal phase lyotropic liquid crystal (LLC)
@@
   reduce the costs of commercial nanofiltration and reverse osmosis.~\cite{werber_materials_2016}
-
-  % BJC4: even if we could calculate diffusion constants, wouldn't there still be value 
-  % in understanding chemical detail?
-  % BJC4: It might not be a good idea to blame our need for this modeling on non-linear MSDs, 
-  % especially since our MSDs appear to be at or nearing a linear regime.
-  % BJC4: seems like we should be addressing the problem as short time scale subdiffusive 
-  % dynamics that dictates measurable long time scale diffusion. Although curves become linear,
-  % the slopes should be a product of the short time scale motion.
-  %MRS: OK, did a pass below, reorganizing it a bit.  See what you think. I think it's OK to talk
-  %about subdiffusion because it's general problem, we aren't making claims about this one. 
-  %BJC6: looks good!
 
@@
   a series of latent, or hidden, states dependent only on the previous state.~\cite{rabiner_tutorial_1989}
-  Propagating an HMM generates sequential but independent observations from 
-  the emission distributions associated with each hidden state. Transitions 
-  between states are mathematically defined by a matrix of transition probabilities.
-  Given a series of observations and a known number of hidden states, the 
+  Propagating an HMM generates sequential but conditionally independent observations from 
+  the emission distributions associated with each hidden state. 
+  Within an HMM, dynamics (i.e. temporal dependence) are modeled solely through  
+  a matrix of transition probabilities. Given a series of observations and a known number of hidden states, the 
   Baum-Welch algorithm, an expectation maximization technique, is a commonly 
   used way to determine the hidden state sequence and the underlying parameters of
-  a standard HMM,~\cite{baum_maximization_1970} though it is also possible to achieve the same
-  results using a Bayesian framework.~\cite{scott_bayesian_2002,jasra_markov_2005} 
+  a standard HMM.~\cite{baum_maximization_1970} However, it is also possible to infer
+  HMM parameters through a Bayesian framework.~\cite{scott_bayesian_2002,jasra_markov_2005} 
   One can also place priors on the transition probabilities and parameters of the hidden 
@@
 
-  By placing a hierarchical Dirichlet process (HDP) prior on the transition 
-  probabilities, it is possible to extend HMMs to an unknown number of hidden
+  By placing a hierarchical Dirichlet process (HDP) prior on the observed time
+  series data, it is possible to extend HMMs to an unknown number of hidden
   states, thus allowing the model's complexity to be driven by the complexity
-  of the data.~\cite{teh_hierarchical_2006} We will refer to this as the HDP-HMM,
-  although in literature it is often called the infinite hidden Markov 
-  model.~\cite{beal_infinite_2002} The HDP-HMM elegantly overcomes the main
-  shortcoming of standard HMMs, the need to choose the number of states 
-  \textit{a priori}, making its use more advantageous in a diversity of 
-  applications including economic data and single particle trajectory 
+  of the data.~\cite{teh_hierarchical_2006} We will refer a model calibrated with
+  this type of prior as an HDP-HMM; this model class is sometimes referred to
+  as an infinite hidden Markov model.~\cite{beal_infinite_2002} The HDP-HMM 
+  elegantly overcomes the main shortcoming of standard HMMs, the need to choose
+  the number of states \textit{a priori}, making its use more advantageous in
+  a diversity of applications including economic data and single particle trajectory 
   analysis.~\cite{shi_identifying_2016,hines_analyzing_2015}
@@
   state sequence representations that do a poor job of describing the 
-  observations. Fox et al. addressed this issue by adding a `sticky' 
+  observations.
+  %BJC: added by Chris  
+  Rapid state switching in the original HDP-HMM not only reduces the predictive
+  ability of the model, but it is also physically unrealistic and can complicate
+  model interpretation. 
+  Fox et al. addressed this issue by adding a `sticky' 
   parameter.~\cite{fox_sticky_2007} The sticky HDP-HMM is useful in situations
@@
 
-  The utility of the sticky HDP-HMM has been further extended to include 
-  temporal dependencies common to many real datasets. State dynamics and 
-  relaxation into new states are often correlated.~\cite{calderon_data-driven_2014}
-  Fox et al. formulated a method that accounts for this behavior by
-  incorporating Markov jump linear systems (MJLSs) into infinite state 
-  models.~\cite{fox_nonparametric_2009} An MJLS models each dynamical mode
-  as a linear dynamical process. Two MJLS sub-classes are switching linear
-  dynamical systems (SLDSs) and switching vector autoregressive (VAR) processes.
-  Switching VAR processes are similar to SLDSs except that they do not
+  The utility of the sticky HDP-HMM has been further extended to account for
+  inherent temporal dependence between measurements common to many time series
+  datasets. 
+  %BJC: reworked by Chris
+  For example, in both MD and single particle tracking, there is strong temporal
+  dependence/correlation between successive measurements even within a 
+  fixed state.~\cite{calderon_data-driven_2014}
+  Fox et al. formulated a method that accounts for temporal dependence betwee
+  successive observations by incorporating Markov jump linear systems (MJLSs)
+  into infinite state models.~\cite{fox_nonparametric_2009} An MJLS models 
+  each dynamical mode as a linear dynamical process. Two MJLS sub-classes are 
+  switching linear dynamical systems (SLDSs) and switching vector autoregressive
+  (VAR) processes. Switching VAR processes are a sub-class of SLDSs that do not
   incorporate measurement noise. Since MD simulations do not contain measurement
@@
 
+  % BJC: fair number of changes to this paragraph based on Chris' suggestions.
+  % BJC: he really wants use to emphasize our contribution with this part
   To our knowledge, applying the HDP-AR-HMM in order to gain kinetic and
@@
   before. Typical applications of the HDP-AR-HMM center around determining the 
-  number of states, the state sequence and occasional analysis of the emission 
+  number of states, the state sequence and analysis of the emission 
   distributions of a time series. The addition of temporal correlation to 
   the inference procedure has primarily been used to improve state sequence 
-  identification.~\cite{calderon_inferring_2015,hamada_modeling_2016}
-  In our approach, we use the HDP-AR-HMM to segment MD time series into distinct
-  dynamical modes, and we cluster and analyze the temporally-correlated 
-  parameters of the model in order to learn physical mechanisms and describe
-  solute kinetics. We can use the model parameters determined either before 
-  or after clustering to generate new time series trajectories which enable 
-  projections of the MD-generated time series to arbitrary length time scales.
+  identification.~\cite{calderon_inferring_2015} In our approach, we use the
+  HDP-AR-HMM not only to segment a collection of MD time series into distinct 
+  dynamical modes, but to uncover unknown transport mechanisms and create 
+  improved predictive models. We cluster the parameters of individual states
+  in order to reduce the total state space down to an interpretable size
+  This allows us to learn the implied dominant physical mechanisms and describe
+  solute kinetics based on interpretation of distinct parameters that dominate
+  the ensemble of MD trajectories. We can use the model parameters determined 
+  either before or after clustering to generate new time series trajectories 
+  which enable projections of the MD-generated time series to arbitrary length
+  time scales.
 
@@
   simultaneously inferring the VAR parameters of those modes. We use the sticky model
-  in order to emphasize self-transitions since we expect solutes to stay trapped in
-  states for appreciable amounts of time.
+  in order to encourage higher self-transition probabilities since we physically expect
+  solutes to stay trapped in states for appreciable amounts of time.
 
@@
 
-  \textit{State sequence and parameter inference}: We inferred the 
-  state sequence and parameters for each of the 24 solute trajectories independently.
-  Although the HDP-AR-HMM is capable of identifying an infinite number of states, 
-  a Dirichlet process tends to exhibit a ``rich get richer" effect, favoring
-  a fewer number of states.~\cite{dreyer_discovering_2011} By applying the algorithm to each trajectory 
-  independently, we reduce the possibility of lumping together multiple 
-  similar states which we would prefer to stay separated before clustering.
-
-  We ran 2000 iterations of the HDP-AR-HMM procedure on each trajectory which
-  was sufficient in order to arrive at converged state sequences and VAR parameter
-  estimates. By our criteria, the procedure generally converged within 500--1000 iterations. We 
-  evaluated convergence based on when the VAR parameter estimates plateaued. 
-  We detected plateaus using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
+  \textit{State sequence and parameter inference}: We ran 2000 iterations of the
+  HDP-AR-HMM procedure on each trajectory which was sufficient in order to arrive
+  at converged state sequences and VAR parameter estimates. By our criteria, the 
+  procedure generally converged within 500--1000 iterations. We evaluated 
+  convergence based on when the VAR parameter estimates plateaued. We detected 
+  plateaus using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
   on the time series of the individual parameters (Section~\ref{S-section:convergence}
@@
 
-  It is usually beneficial to employ intelligent state sequence initialization procedures. 
-  Most importantly, the states identified by the HDP-AR-HMM are heavily influenced by the 
-  Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. In 
+  It is usually beneficial to employ intelligent state sequence initialization procedures
+  in nonparametric Bayesian approaches.~\cite{fox_bayesian_2010}
+  Most importantly in this work, the states identified by the HDP-AR-HMM are heavily 
+  influenced by the Gaussian prior placed on $\mathbf{c}$ in Equation~\ref{eqn:var}. In 
   Section~\ref{S-section:fitting_tips} of the Supporting Information we outline our 
@@
 
+  %BJC: The following paragraph used to be the first paragraph after italics above. 
+  % I moved it down here as suggested by Chris below. What do you think in terms of flow?  
+  We inferred the state sequence and parameters for each of the 24 solute 
+  trajectories independently. Although the HDP-AR-HMM is capable of identifying 
+  an infinite number of states, a Dirichlet process tends to exhibit a 
+  ``rich get richer" effect, favoring a fewer number of states.~\cite{dreyer_discovering_2011}
+  By applying the algorithm to each trajectory independently, we reduce the 
+  possibility of lumping together multiple similar states which we would prefer
+  to stay separated before clustering. 
+  %BJC: added following sentence to aid reader in response to Chris' question below 
+  In Section~\ref{method:realizations}, we 
+  explain how we use these 24 independent models in order to generate a single
+  MSD prediction.
+  % BJC: abridged Chris comment with respect to this paragraph here:
+  % CPC: the question i have at this point as a reader in this area, given 
+  % how this is setup both as predictive and clustering, is "how do they plan to
+  % generate data and predict with this model if they have 24 different transition
+  % mat estimates"
+  % CPC: returning to comment after reading.  section 2.4 explains what you do 
+  % (though i'm still fuzzy on how you estimate transition matrix probs in method 2). 
+  % (BJC: Note I tried to clarify this process for method 2 below)
+  % CPC_continued: in any case, you might want to avoid obvious critiques and head 
+  % scratching from expert reviewers. i'd suggest moving this paragraph to end of subsection and
+  % expand on above considerations after you've given more cut and dry details below and reference 2.4 stating     
+  %that you say how you simulate from a model estimated one trajectory at a time via HDP-AR-HMM inference
+
   \subsection{State Clustering}\label{method:clustering}
 
-  We clustered states wit like parameter sets in order to reduce the state space to
-  a more easily interpretable size. For each solute studied, we identified approximately 
-  300-500 independent states, each with separate VAR(1) parameters. Many of these states
-  exhibit very similar dynamical behavior except their mean levels in each dimension
-  are different.
+  We clustered states with like parameter sets in order to reduce the state space to
+  a more easily interpretable size 
+  %BJC: added following in response to Chris' below comment. I think I'm interpretting what he's saying right
+  % CPC: perhaps keep hammering home not only reducing, but also reemphasize why absolute
+  % value of some parameters really not of interest 
+  and because the parameters of a single states does not always give meaningful physical insight. 
+  For each solute studied, we identified approximately 300-500 independent states, 
+  each with separate VAR(1) parameters. Many of these states exhibit very similar
+  dynamical behavior except their mean levels in each dimension are different.
 
@@
   We clustered based on the eigenvalues of $A$ and $\Sigma$, the distance from the 
-  pore center and the self-transition probabilities, $T_{ii}$, of each state. $A$ 
-  and $\Sigma$ capture the correlation and size of fluctuations. $T_{ii}$ is directly
-  related to the expected time spent in each state. The distance from the closest pore 
-  center is likely meaningful since the membrane is radially inhomogeneous from each 
-  pore, transitioning from hydrophilic pores to hydrophobic tails. However, the 
-  channels are isotropic along the pore axis so we do not cluster in means in the 
-  $z$ dimension. We normalized each clustering dimension by its variance and shifted
-  the mean to zero.
-
-  To take advantage of the system's cylindrical symmetry, we converted the parameters that
-  are directly related to solute position into cylindrical coordinates before clustering. 
+  pore center and the self-transition probabilities, $P_{ii}$, of each state. $A$ 
+  and $\Sigma$ quantify the temporal correlation and size of fluctuations in a 
+  given state. $P_{ii}$ is directly related to the expected time spent in each state.
+  The distance from the closest pore center is expected to be physically meaningful
+  since the membrane is radially inhomogeneous from each pore, transitioning from 
+  hydrophilic pores to hydrophobic tails. However, the channels are isotropic along
+  the pore axis so we do not cluster in means in the $z$ dimension. Before carrying
+  out the agglomerative clustering algorithm, we normalized each clustering dimension
+  by its variance and shifted the mean to zero.
+
+  %BJC: small modifications to this paragraph for clarity
+  We converted the parameters that are directly related to solute position into 
+  cylindrical coordinates and cast them in the same units before clustering. 
   We replaced the $x$ and $y$ eigenvalues of $\Sigma$ and $A$ with $\lambda_x$ + 
   $\lambda_y$ and $\lambda_x^2$ + $\lambda_y^2$ respectively, which are invariant with 
-  rotation around the $z$ axis. We clustered on squared means in $r$, 
-  $\mu_r^2 = \mu_x^2 + \mu_y^2$, rather than $\mu_x$ and $\mu_y$ individually, with the
-  square $\mu_r$ converting it into the same units as $A$ and $\Sigma$.
-
-  To cluster on $T_{ii}$, we first cast it in terms of the expected dwell times. The expected
+  rotation around the $z$ axis. We clustered on the squared means in $r$, $\mu_r^2 = 
+  \mu_x^2 + \mu_y^2$, where $\mu_r$, $\mu_x$ and $\mu_y$ are the means in $r$, $x$ and
+  $y$ respectively.
+%  rather than $\mu_x$ and $\mu_y$ individually, with the
+%  square $\mu_r$ converting it into the same units as $A$ and $\Sigma$.
+
+  To cluster on $P_{ii}$, we first cast it in terms of the expected dwell times. The expected
   value of the number of sequential self-transitions is simply:
   \begin{equation}  
-   E[dwell~time] = \frac{1}{1 - T_{ii}}
+   E[dwell~time] = \frac{1}{1 - P_{ii}}
    \label{eqn:dwell_times}
   \end{equation}  
-  This relationship implies that dwell times approach infinity as $T_{ii}$ approaches
+  This relationship implies that dwell times approach infinity as $P_{ii}$ approaches
   1. Therefore we found the most success with agglomerative clustering by linearizing this
-  relationship and clustering on $-\log(1 - T_{ii})$.
+  relationship and clustering on $-\log(1 - P_{ii})$.
 
@@
 
-  \textit{Obtaining Parameters of Clustered States}: We remapped and fixed the
-  state sequence based on the cluster assignments and 
-  parameterized the clusters using the inference component of the HDP-AR-HMM algorithm.
-  First, we modified the ($x$, $y$, $z$) solute trajectories so that they had a 
-  mean of zero, leaving only the fluctuations. We took advantage of the
-  rotational invariance of the system by rotating the coordinates about the pore 
-  axis such that the mean ($x$, $y$) vector of each separate segment was aligned with the 
-  $x$ axis, forcing the $y$ component to zero. Next, we subtracted the means from 
-  each separate segment in the $x$ and $z$ dimensions. We used
-  the inference component of the HDP-AR-HMM algorithm on this modified trajectory to 
-  infer the clustered state parameters by fixing the clustered state sequence. See
-  Section~\ref{S-section:ihmm_procedure} for figures illustrating this process.
-
-  We obtained $\mathbf{c}$ vectors of the clustered states by averaging each 
-  value of the rotated $\mathbf{c}$ vectors assigned to the same cluster. Note
-  that we only care about the $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$ because
-  solute trajectories are not bound in the $z$ direction.
+  %BJC: reworked this section for better clarity as it confused Chris
+  \textit{Obtaining Parameters of Clustered States}: We obtained the 
+  mean vectors, $\mathbf{c}$, of the clustered states by averaging each 
+  value of the $\mathbf{c}$ vectors assigned to the same cluster. Note 
+  that we only care about the $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$ 
+  because solute trajectories are not bound in the $z$ direction.
+
+  In order to determine $A$ and $\Sigma$ of the clusters, we modified the 
+  ($x$, $y$, $z$) solute trajectories to have a mean of zero, leaving only
+  the fluctuations. This is necessary since the states which constitute each 
+  cluster have different means, $\mathbf{c}$, and the parameterization of 
+  the clustered states relies on contributions by the fluctuations from all
+  its constituents. We zeroed the trajectories in two steps. First, we took 
+  advantage of the rotational invariance of the system by rotating the coordinates
+  about the pore axis such that the mean ($x$, $y$) vector of each separate 
+  segment was aligned with the $x$ axis, forcing the $y$ component to zero 
+  (see Figure~\ref{S-fig:y_zeroed}). Second, we subtracted the means from each
+  separate unclustered segment in the $x$ and $z$ dimensions 
+  (see Figure~\ref{S-fig:xyz_zeroed}).
+
+  We obtained estimates of clustered $A$ and $\Sigma$ parameters as well as a
+  single $T$, describing transitions between all possible clustered states exhibited by
+  the ensemble of trajectories, using the inference component of the HDP-AR-HMM
+  algorithm. We applied the HDP-AR-HMM simultaneously on all 24 zeroed solute
+  trajectories with state sequences fixed according to the remapped clustered 
+  state assignments. This is only possible because the state sequence is fixed. 
+  In cases where one does not know the state sequence and would like to 
+  incorporate data from multiple trajectories, one can apply the beta process (BP)
+  AR-HMM.~\cite{fox_sharing_2009} However the data requirements may be quite high
+  for a good parameterization, which is why we elected to follow the clustering 
+  approach described thus far.
+  %BJC: I actually found 3 different ways do this. All giving the same results.
+  % Method 1: described above - this is the most efficient way
+  % Method 2: Link all 24 trajectories by adding a coffin state (basically a 
+  % state that is a vector of zeros) between each traj
+  % Method 3: Parameterize each trajectory independently, average together. T is
+  % estimated by making a count matrix based on inputs from each trajectory
+
+%  In Section~\ref{S-section:ihmm_procedure} of the Supporting
+%  Information, we provide a step-by-step illustration of the following process.
 
@@
   and quantitatively different from those generated by unclustered parameter sets.
+  %BJC: added based on Chris' suggestion.
+  For the purposes of our analysis, we assume ergodicity of the 24 solute trajectories.
+  That is, we assume our MD simulations sample all possible states with the correct 
+  frequency.
   In our discussion we evaluate both methods:
@@
   For both approaches, we drew state sequences with transition probabilities given 
+  % BJC: Chris wasn't clear where T came from for method 2. I tried to make it clearer in 
+  % last paragraph of previous section. Let me know if it's not
   by $T$ of the HDP-AR-HMM. While in a given state, we simulated motion according to the 
@@
   displacements over time lag $\tau$:
+  %BJC: I changed T -> L in following equation since T is the transition matrix
   \begin{equation}
-  	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
+  	\overline{z^2(\tau)} = \dfrac{1}{L - \tau}\int_{0}^{L - \tau} (z(t + \tau) - z(t))^2 dt
   \label{eqn:tamsd}
   \end{equation}
-  where T is the length of the trajectory.
+  where $L$ is the length of the trajectory.
 
@@
   similar to the MD trajectories to which they were fit. It is important that our
-  model reproduces this behavior so that we can have confidence in its usefulness
-  for quantitative predictions.
+  model reproduces this behavior so that we can have confidence in its potential
+  usefulness for more quantitative predictions.
 
@@
   %BJC6: added. Should I add a figure?
-  A potential shortcoming of the HDP-AR-HMM is its inability to reproduce the 
-  short time scale MSD curves. The MSDs predicted by the model tend to enter
-  a linear regime much more quickly than the MD MSDs (see 
-  Figure~\ref{S-fig:unclustered_msd_shortlag} of the Supporting Information
+  A potential shortcoming of the HDP-AR-HMM applied to MD simulations is its 
+  inability to reproduce the short time scale MSD curves. The MSDs predicted
+  by the model tend to enter a linear regime much more quickly than the MD MSDs
+  (see Figure~\ref{S-fig:unclustered_msd_shortlag} of the Supporting Information
   for example). This is not a major concern for predicting macroscopic properties
@@
   \textit{The dynamics of frequently occurring states}: We may learn the most by 
-  studying the dynamical modes common to the majority of the solute trajectories.
-  Of the 10 state clusters, only 5 appear in a significant number of solute 
+  studying the dynamical modes common to the majority of methanol trajectories.
+  Of the 10 state clusters, only 5 are sampled by a significant number of 
   trajectories (Figure~\ref{fig:prevalence}). All of which are present in 
@@
   \includegraphics[width=0.5\textwidth]{prevalence.pdf}
-  \caption{5 out of the 10 clustered states are visited by 15 or more of the solute
+  \caption{5 out of the 10 clustered states are visited by 15 or more of the methanol
   trajectories (States 1--5). Although a majority of the solutes visit these 5 
@@
   \end{subfigure}
+  %BJC: Is it worth putting a bars with the solute MSDs on this plot
   \begin{subfigure}{0.49\textwidth}
@@
   their time close to the pore center. Only methanol has a significant density
-  far from the pore center. (c) The largest expected value (see~\ref{eqn:dwell_times})
-  of dwell times among the dominant clustered states for each solute are inversely
-  related to the solute's MSD. 
+  far from the pore center. (c) The largest expected value (see 
+  Equation~\ref{eqn:dwell_times}) of dwell times among the dominant clustered 
+  states for each solute are inversely related to the solute's MSD. 
+  % BJC: Copying Chris' comments below:
+  % CPC: Discussion is confusing. guessing error bars are from measured simulation 
+  % dwell times in dominant state.  
+  % BJC: will add error bar explanation once I figure out exactly how to modify the figure
+  % CPC: what if trajectory has more than one dominant state? (seems from fig like 
+  % you take one with largest dwell time from your model. 
+  % BJC: All solutes have at  least 4 dominant states by my definition. maybe it would 
+  % be better to sample dwell times from all of the dominant states. Just weight 
+  % their contributions. Not sure if weighting should be with respect to the fraction
+  % the total simulation time spent in each state, or the number of times the state
+  % was visited.
+  % CPC: might want to better connect MSDs of model in fig.3 to fig 9 c and 
+  % expand/clarify discussion on connection of fig 9c to other panels just lots
+  % of ambiguity here, but results seem promising.
+  % BJC: is it worth plotting bars with the MSD after 1000 ns as part of (c)? 
   %MRS5: not clear what ``largest expected'' means here.
@@
 
+  % BJC: Chris was confused by this paragraph
   Solutes with dominant states characterized by long dwell times tend to 
-  have lower MSDs. In Figure~\ref{fig:dwell_time_summary}, we plot the expected dwell
-  time of each solute in the dominant state which has the the highest 
-  self-transition probability. We define the dominant states as any states that
-  are visited by more than half of the solute trajectories. The trend in MSDs is
-  inversely related to the trend in maximum expected dwell times. Both acetic acid
-  and urea participate in many hydrogen bonds and sodium ion association interactions
-  and the states visited by both solutes have similar distributions of radial means,
-  however acetic acid is subject to much longer dwell times, and hence a lower MSD. 
-  This may be because acetic acid is a stronger hydrogen bond donor than urea.
+  have lower MSDs. We define the dominant states exhibited by each solute
+  as any state visited by at least half (12) of the solute trajectories.
+  By our definition and based on our choice to study 10 clusters for each 
+  solute, methanol, ethylene glycol, urea and acetic acid are characterized
+  %BJC: added this supporting figure 
+  by 5, 6, 5 and 4 dominant states respectively (see Figure~\ref{fig:state_prevalence}
+  of the Supporting Information). In Figure~\ref{fig:dwell_time_summary}, we
+  plot the expected dwell time of each solute in the dominant state which 
+  has the the highest self-transition probability. The MSDs shown in 
+  Figure~\ref{fig:unclustered_msds} are inversely related to the maximum 
+  expected dwell times. Both acetic acid and urea participate in many hydrogen
+  bonds and sodium ion association interactions and the states visited by both 
+  solutes have similar distributions of radial means, however acetic acid is 
+  subject to much longer dwell times, and hence a lower MSD. This may be 
+  because acetic acid is a stronger hydrogen bond donor than urea.
 

### 2020-05-26 Ben_Manuscripts/hdphmm/cover_letter.tex
adding draft of cover letter

--- 2020-04-29 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
@@
 	%\noindent May 3\textsuperscript{rd}, 2019\\
-	\noindent \today \\
+	\noindent \today
 
@@
 
-	\newcommand{\ManuscriptTitle}{Capturing Subdiffusive Solute Dynamics and 
-	Predicting Selectivity in Nanoscale Pores with Time Series Modeling}
+	\newcommand{\ManuscriptTitle}{Statistical Inference of Transport Mechanisms and
+	Long Time Scale Behavior from Time Series of Solute Trajectories in 
+	Nanostructured Membranes}
 
-	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia
-        and Michael R.  Shirts, for consideration for publication as
-        an Article in the Journal of Chemical Theory and
-        Computation. We expect this work to be of significant interest
-        to researchers who study complex transport at the molecular
-        level, as it describes important new approaches for estimating long
-        time scale behavior and bulk transport behavior from shorter
-        molecular trajectories exhibiting anomalous diffusion rather
-        than Brownian motion. Please note that this article has been
-        uploaded to arXiv with differences only in formatting:
-        \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\
+	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia, Christopher P.
+	Calderon and Michael R. Shirts, for	consideration for publication as a Research
+	Article in the ``Machine Learning in Physical Chemistry" special issue of the Journal 
+	of Physical Chemistry, specifically in section X of % BJC: the link with section titles is an unfinished webpage
+	part B of the journal. We expect this work to be of significant interest to 
+	researchers who study complex dynamics in both structured and amorphous soft 
+	materials. %BJC: this could be made more general. Maybe better focused for JPC though
 
-	In this article, we analyze solute trajectories generated from
-        5$\mu$s molecular dynamics (MD) simulations of an inverted
-        hexagonal (H\textsubscript{II}) phase self-assembled lyotropic
-        liquid crystal (LLC) polymer membrane to parameterize two
-        different stochastic time series approaches capable of
-        predicting solute flux and selectivity on a macroscopic
-        scale. Both approaches quantitatively reproduce the mean
-        squared displacements (MSDs) exhibited by solutes in MD
-        simulations. This is among the first studies to apply time
-        series modeling of molecular simulations in order to infer
-        behavior at long time scales and estimate bulk
-        materials properties with complex anomalous diffusion
-        mechanisms.\\
+	In this article, we apply the sticky hierarchical Dirichlet process autoregressive
+	hidden Markov model (HDP-AR-HMM), a non-parametric Bayesian time series
+	classification technique, to solute center-of-mass trajectories generated from
+	5 $\mu s$ molecular dynamics (MD) simulations in a cross-linked inverted hexagonal
+	phase lyotropic liquid crystal (LLC) membrane in order to automatically detect a
+	variety of solute dynamical modes. We can use this information in order to 
+	better understand the complex transport mechanisms exhibited by the solutes in 
+	our simulation which will greatly increase the efficiency with which we 
+	design LLC membranes for solute-specific separations.
 
-	This article builds on recent work of ours published in
-        J. Phys. Chem. B where we characterized transport mechanisms
-        exhibited by a series of small polar solutes in an LLC
-        Membrane (Coscia and Shirts \textit{J. Phys.  Chem. B}, 123,
-        6314--6330 (2019)). In this work, we build on the chemical
-        intuition gained from our previous study in order to formulate
-        stochastic models which produce trajectory realizations that
-        share the same dynamical properties as those exhibited by
-        solutes in our MD simulations. We explore two main modeling
-        approaches. First, using anomalous diffusion theory, we
-        parameterize solute motion as subordinated fractional Brownian
-        and L\'evy motion processes, based on the observation that
-        solutes experience a series of dwell times separated by
-        anti-correlated hop lengths. Secondly, we add state-dependent
-        dynamics to standard Markov state modeling approaches, where
-        we model solute motion as a series of transitions between
-        various trapped states, each with different dynamical
-        properties.  Finally, we demonstrate how one can project models 
-        onto macroscopic timescales in order to estimate
-        solute flux and selectivity.\\
+	Our work represents a considerable advancement over our most recent study 
+	characterizing the same set of solute center-of-mass time series trajectories
+	(Coscia and Shirts, arXiv:2004.07905 [cond-mat.soft]). % BJC: is this the right way to cite arXiv?
+	In that work, we used our qualitative understanding of solute transport 
+	(Coscia and Shirts \textit{J. Phys. Chem. B}, 123, 6314--6330 (2019)) in order
+	to formulate stochastic models which could be used to project solute behavior
+	on macroscopic time scales, thus allowing prediction of experimentally relevant
+	properties like membrane selectivity. Using the HDP-AR-HMM, we can analyze solute
+	trajectories with no prior knowledge of their dynamic behavior and easily produce
+	models which quantitatively describe their long time scale dynamics. Since the 
+	approach is non-parametric, the complexity of our data drives the complexity of
+	the model. We cluster the parameter sets in order to reduce the total space of 
+	dynamical states to a small set of distinct parameters which allow us to clearly
+	understand physical	mechanisms in terms of solute-membrane interactions. To our 
+	knowledge, this is the first application of the HDP-AR-HMM to MD data and it is
+	the first time this framework has been used to gain both mechanistic and kinetic
+	insight.
 
 	%BJC: included phone numbers because it asked to do so in author's guide.
+	%BJC: need at least 5 reviewers
 	\noindent Some suggestions for reviewers are:
@@
 
+	    %BJC: these are reviewers suggested for the first stochastic transport paper
+	    %BJC: not sure if bad to use twice
 		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
 		and transport under confinement within various nanostructured materials 
-		(Northeastern University, 617-373-8619,\\ \href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})
+		(Northeastern University, 617-373-8619,\\ \href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu}).
 
@@
 		proton transport in nanostructured and charged polymer membranes. (The University of Tennessee 
-		Knoxville, 865-974-2026, \href{mailto:spaddison@utk.edu}{spaddison@utk.edu})
+		Knoxville, 865-974-2026, \href{mailto:spaddison@utk.edu}{spaddison@utk.edu}).
+
+		\item Coray Colina uses various simulation techniques to understand structure-property relations
+		in functional materials including nanoporous materials for separation applications. (University
+		of Florida, 352-294-3488, \href{mailto:colina@chem.ufl.edu}{colina@chem.ufl.edu}).
+
+		\item Venkat Ganesan uses multiscale modeling to study solute and ion transport in complex
+		nanostructured morphologies in order to learn how to design novel materials. (The University
+		of Texas at Austin, 512-471-4856, \href{mailto:venkat@che.utexas.edu}{venkat@che.utexas.edu}).
+
+		%BJC: from structure paper
+		\item Eric Jankowski has experience modeling soft materials using molecular dynamics
+		including work done simulating structure factors from simulations, much like
+		the techniques we use in our work (Boise State University, 208-426-5681,
+		\href{mailto:ericjankowski@boisestate.edu}{ericjankowski@boisestate.edu})
+
+		\item Emily Fox?  % she made the HDP-AR-HMM
 
@@
 	\noindent Benjamin J. Coscia \\
+	\noindent Christopher P. Calderon \\
 
@@
 
-% LocalWords:  BJC Subdiffusive Solute Nanoscale Coscia arXiv solute lyotropic
-% LocalWords:  LLC MSDs solutes Phys Chem subdiffusive evy timescales Klafter
-% LocalWords:  univeristy JPCB woould nanostructured Mahesh Mahanthappa klafter
-% LocalWords:  Tel Paddison
+% LocalWords:  BJC

### 2020-05-28 Ben_Manuscripts/hdphmm/Draft.tex
Comments.

@@
   in each state and position within the inhomogeneous membrane structure. We analyze
-  prevalent clusters in order to relate their parameters to physical interactions between 
+  prevalent clusters in order to relate their 
+  %MRS: suggestion to add:
+  dynamical
+  parameters to physical interactions between 
   solutes and the membrane.
@@
   Rapid state switching in the original HDP-HMM not only reduces the predictive
-  ability of the model, but it is also physically unrealistic and can complicate
+  ability of the model, but 
+  %MRS: tweaked; sometimes it might be physical.
+  % it
+  in many cases
+  is also physically unrealistic and can complicate
   model interpretation. 
@@
   % BJC: fair number of changes to this paragraph based on Chris' suggestions.
-  % BJC: he really wants use to emphasize our contribution with this part
+  % BJC: he really wants us to emphasize our contribution with this part
   To our knowledge, applying the HDP-AR-HMM in order to gain kinetic and
@@
 
-  It is usually beneficial to employ intelligent state sequence initialization procedures
+  It is usually beneficial to employ 
+  %MRS: tweak
+  %intelligent 
+  well-informed
+  state sequence initialization procedures
   in nonparametric Bayesian approaches.~\cite{fox_bayesian_2010}
@@
   trajectories independently. Although the HDP-AR-HMM is capable of identifying 
-  an infinite number of states, a Dirichlet process tends to exhibit a 
+  an infinite number of states, a Dirichlet process 
+  %MRS: tweak
+  %tends to exhibit a 
+  exhibits a 
   ``rich get richer" effect, favoring a fewer number of states.~\cite{dreyer_discovering_2011}
+  %MRS: this next sentence is a bit vauge.  Why would we prefer thtem to stay separated?
   By applying the algorithm to each trajectory independently, we reduce the 
@@
   % value of some parameters really not of interest 
+  %MRS: explain why parameters of single states don't give insight; more context needed?  Is CPC talking about
+  %MRS: some some of the parmameters not being interesting in general, not just the values for some states?
   and because the parameters of a single states does not always give meaningful physical insight. 
@@
   We obtained estimates of clustered $A$ and $\Sigma$ parameters as well as a
+  %MRS: did you mean to change to T to P here?
+  %MRS: also, maybe ``consensus'' or ``merged'' instead of ``single''
   single $T$, describing transitions between all possible clustered states exhibited by
@@
   trajectories with state sequences fixed according to the remapped clustered 
-  state assignments. This is only possible because the state sequence is fixed. 
+  state assignments. 
+  %MRS: be specific what ``This'' is in the sentence.
+  This is only possible because the state sequence is fixed. 
   In cases where one does not know the state sequence and would like to 
@@
   % last paragraph of previous section. Let me know if it's not
+  %MRS: P vs. T agin?
   by $T$ of the HDP-AR-HMM. While in a given state, we simulated motion according to the 
@@
   MSD of the realizations of our models enters a linear regime near a 5 ns time lag
+  %MRS: ref below to figure not recognized?
   (see Figure~\ref{S-fig:MET_nclusters} of the Supporting Information for example).
@@
   %BJC6: added. Should I add a figure?
+  %MRS: I think fine as supporting.
   A potential shortcoming of the HDP-AR-HMM applied to MD simulations is its 
@@
 
-  The data suggests that the particular LLC membrane studied in this work is
-  capable of selectively separating urea and acetic acid from ethylene glycol
+  %MRS: I feel like this should be caveatted a bt. 
+  The data suggests that the particular LLC membrane studied in this work, 
+  up to the resolution of the moleceular modeling,
+  is capable of selectively separating urea and acetic acid from ethylene glycol
   and methanol. Ethylene glycol and methanol have comparable diffusivities
@@
      \item This state's radial mean of 2.4 nm implies that it occurs exclusively in the
-     tail region based. Its fluctuations are small and there is little past hop dependence.
+     tail region based. Fluctuations are small and there is little past hop dependence.
      \item This is likely a hopping state that strongly contributes to the solute's MSD. 
@@
      \item This is an intermediate-length trapping state that occurs 0.9 nm from the pore 
-     center on average. It's fluctuations are tight and relatively independent of its previous 
+     center on average. Fluctuations are small and relatively independent of its previous 
      fluctuation.
@@
   states for each solute are inversely related to the solute's MSD. 
+  %MRS: is the c) point actually made in the figure?  There's no MSD in that graph.  
   % BJC: Copying Chris' comments below:
@@
   % BJC: is it worth plotting bars with the MSD after 1000 ns as part of (c)? 
-  %MRS5: not clear what ``largest expected'' means here.
-  %BJC6: modified to 'expected value' and referenced equation   
   (d) The expected dwell time of solutes increases 
@@
   % BJC: Chris was confused by this paragraph
+  %MRS: maybe switch ``dominant'' for something else, like predominant, or consensus
   Solutes with dominant states characterized by long dwell times tend to 
@@
   %BJC: added this supporting figure 
+  %MRS: for some reason Not referencing this figure in supporting despite xr? 
   by 5, 6, 5 and 4 dominant states respectively (see Figure~\ref{fig:state_prevalence}
@@
   When clustering, our goal was to create the simplest model possible that gave
-  clear mechanistic insight. This is important for systems where transport mechanisms
+  clear mechanistic insight. This is particularly important for systems where transport mechanisms
   are not easily hypothesized. However, once one gains some mechanistic understanding,

### 2020-05-28 Ben_Manuscripts/hdphmm/Draft.tex
Modified figures and edits for clarity

--- 2020-05-26 Ben_Manuscripts/hdphmm/Draft.tex
@@
 \author{Christopher P. Calderon}
-\affiliation{Ursa Analytics, Inc., Denver, CO 80212, USA} %CPC:  > 90% of my time spent officially under Ursa 
+\affiliation{Ursa Analytics, Inc., Denver, CO 80212, USA}
 \alsoaffiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
@@
   in each state and position within the inhomogeneous membrane structure. We analyze
-  prevalent clusters in order to relate their parameters to physical interactions between 
-  solutes and the membrane.
+  predominate clusters in order to relate their dynamical parameters to physical
+  interactions between solutes and the membrane.
 
@@
   brackish water desalination, separation of organic micropollutants from 
-  municipal water supplies, recovering valuable dissolved species from 
-  waste streams and creating breathable barriers to harmful contaminants are just a
+  municipal water supplies, recovery of valuable dissolved species from 
+  waste streams and the creation of breathable barriers to harmful contaminants are just a
   subset of the broad range of applications for selective membrane separations.~\cite{fritzmann_state---art_2007,fonseca_couto_critical_2018,dischinger_evaluation_2019,ramaseshan_functionalized_2006}
@@
 
-  In this work we attempt uncover similar physical meaning through a data-driven process. 
+  In this work we attempt to uncover similar physical meaning through a data-driven process. 
   We utilize the sticky hierarchical Dirichlet process autoregressive hidden Markov model 
@@
   autoregressive (VAR) modes present in solute center-of-mass MD 
-  trajectory.~\cite{fox_bayesian_2010} The sticky HDP-AR-HMM greatly extends the 
+  trajectories.~\cite{fox_bayesian_2010} The sticky HDP-AR-HMM greatly extends the 
   basic framework of simpler but more limited finite hidden Markov modeling approaches.
@@
   HMM parameters through a Bayesian framework.~\cite{scott_bayesian_2002,jasra_markov_2005} 
-  One can also place priors on the transition probabilities and parameters of the hidden 
+  One can place priors on the transition probabilities and parameters of the hidden 
   states' emission distributions in order to iteratively infer their values and to
@@
   a diversity of applications including economic data and single particle trajectory 
-  analysis.~\cite{shi_identifying_2016,hines_analyzing_2015}
+  analysis.~\cite{shi_identifying_2016,hines_analyzing_2015,sgouralis_introduction_2017,jazani_alternative_2019,wang_single-molecule_2014,persson_extracting_2013}
 
@@
   state sequence representations that do a poor job of describing the 
-  observations.
-  %BJC: added by Chris  
-  Rapid state switching in the original HDP-HMM not only reduces the predictive
-  ability of the model, but it is also physically unrealistic and can complicate
-  model interpretation. 
+  observations. Rapid state switching in the original HDP-HMM not only 
+  reduces the predictive ability of the model, but in many cases is also 
+  physically unrealistic and can complicate model interpretation. 
   Fox et al. addressed this issue by adding a `sticky'
@@
   inherent temporal dependence between measurements common to many time series
-  datasets. 
-  %BJC: reworked by Chris
-  For example, in both MD and single particle tracking, there is strong temporal
-  dependence/correlation between successive measurements even within a 
-  fixed state.~\cite{calderon_data-driven_2014}
+  datasets. For example, in both MD and single particle tracking, there is 
+  strong temporal dependence/correlation between successive measurements even
+  within a fixed state.~\cite{calderon_data-driven_2014}
   Fox et al. formulated a method that accounts for temporal dependence betwee
@@
 
-  % BJC: fair number of changes to this paragraph based on Chris' suggestions.
-  % BJC: he really wants use to emphasize our contribution with this part
   To our knowledge, applying the HDP-AR-HMM in order to gain kinetic and
@@
   HDP-AR-HMM not only to segment a collection of MD time series into distinct 
-  dynamical modes, but to uncover unknown transport mechanisms and create 
+  dynamical modes, but to uncover unknown transport mechanisms and to create 
   improved predictive models. We cluster the parameters of individual states
@@
 
+  % BJC: Michael prefers not to put any conclusions in the intro. So we basically pose
+  % questions to which we already know the answer, with the intent of readers having
+  % a better sense of what to look for while reading.
   We aim to address two primary scientific questions with this work:
   \begin{enumerate}
+
   \item First, we want to know whether it is possible to use the HDP-AR-HMM to 
@@
   regular diffusive behavior again occurs.
+
   \item Second, we want to know if the HDP-AR-HMM algorithm can help
   efficiently uncover underlying transport mechanisms which give rise to different 
-  solute dynamical behavior.
-  We use the parameters of the states identified by the HDP-AR-HMM in order to infer 
-  dominant solute-membrane interactions and transport mechanisms. We cluster similar 
-  state parameters in order to reduce the state space and to understand which segments 
-  of the solute trajectories exhibit similar behavior. We support our mechanistic 
-  hypotheses via quantitative comparison to various physical membrane properties and
-  solute-membrane interactions.
+  solute dynamical behavior. We cluster similar state parameters across all
+  trajectories in order to reduce the total state space and to understand which
+  segments of the solute trajectories exhibit similar behavior. We use the 
+  parameters of the clustered states identified by the HDP-AR-HMM in order to 
+  infer dominant solute-membrane interactions and transport mechanisms. We 
+  support our mechanistic hypotheses via quantitative comparison to various 
+  physical membrane properties and solute-membrane interactions.
+
   \end{enumerate}
@@
   We implemented the sticky HDP-AR-HMM in Python 
-  (\texttt{https://github.com/bencoscia/hdphmm}) which we heavily adapted from
+  (\texttt{https://github.com/shirtsgroup/hdphmm}) which we heavily adapted from
   the MATLAB code of Fox et al.~\cite{fox_nonparametric_2009} Since we do not incorporate
@@
   the HDP-AR-HMM and related models.~\cite{fox_bayesian_2010} 
-  %MRS: possibly should give the permanent reference to a shirtsgroup fork?  We can discuss which is likely to be more permanent  
   All other post-simulation trajectory analysis tools are available online at
@@
   10\% water by weight. Approximately one third of the water molecules 
-  occupy the tail region with the rest near the pore center.~\cite{coscia_chemically_2019}
+  occupy the tail region with the rest are near the pore center.~\cite{coscia_chemically_2019}
 
@@
   of solutes per pore provides a sufficient amount of data from which to generate 
-  statistics on the time scales which we simulate and prevents solute clustering
-  facilitating our study of pure solute-membrane interactions. Further details on
-  the setup and equilibration of these systems are detailed in our previous work.~\cite{coscia_chemically_2019}
+  statistics on the time scales which we simulate and prevents any significant
+  solute clustering facilitating our study of pure solute-membrane interactions. 
+  Further details on the setup and equilibration of these systems are detailed 
+  in our previous work.~\cite{coscia_chemically_2019}
 
@@
   convergence based on when the VAR parameter estimates plateaued. We detected 
-  plateaus using the module \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
-  on the time series of the individual parameters (Section~\ref{S-section:convergence}
+  plateaus using the module \\ \texttt{pymbar.timeseries.detect\_equilibration}~\cite{chodera_simple_2016} 
+  on the time series of the individual parameters (see Section~\ref{S-section:convergence}
   of the Supporting Information). Convergence of the VAR parameters implies that
@@
 
-  It is usually beneficial to employ intelligent state sequence initialization procedures
-  in nonparametric Bayesian approaches.~\cite{fox_bayesian_2010}
+  It is usually beneficial to employ well-informed state sequence initialization 
+  procedures in nonparametric Bayesian approaches.~\cite{fox_bayesian_2010}
   Most importantly in this work, the states identified by the HDP-AR-HMM are heavily 
@@
 
-  %BJC: The following paragraph used to be the first paragraph after italics above. 
-  % I moved it down here as suggested by Chris below. What do you think in terms of flow?  
   We inferred the state sequence and parameters for each of the 24 solute 
   trajectories independently. Although the HDP-AR-HMM is capable of identifying 
-  an infinite number of states, a Dirichlet process tends to exhibit a 
-  ``rich get richer" effect, favoring a fewer number of states.~\cite{dreyer_discovering_2011}
+  an infinite number of states, a Dirichlet process exhibits a ``rich get richer" 
+  effect, favoring a fewer number of states.~\cite{dreyer_discovering_2011}
   By applying the algorithm to each trajectory independently, we reduce the 
-  possibility of lumping together multiple similar states which we would prefer
-  to stay separated before clustering. 
-  %BJC: added following sentence to aid reader in response to Chris' question below 
-  In Section~\ref{method:realizations}, we 
-  explain how we use these 24 independent models in order to generate a single
-  MSD prediction.
-  % BJC: abridged Chris comment with respect to this paragraph here:
-  % CPC: the question i have at this point as a reader in this area, given 
-  % how this is setup both as predictive and clustering, is "how do they plan to
-  % generate data and predict with this model if they have 24 different transition
-  % mat estimates"
-  % CPC: returning to comment after reading.  section 2.4 explains what you do 
-  % (though i'm still fuzzy on how you estimate transition matrix probs in method 2). 
-  % (BJC: Note I tried to clarify this process for method 2 below)
-  % CPC_continued: in any case, you might want to avoid obvious critiques and head 
-  % scratching from expert reviewers. i'd suggest moving this paragraph to end of subsection and
-  % expand on above considerations after you've given more cut and dry details below and reference 2.4 stating     
-  %that you say how you simulate from a model estimated one trajectory at a time via HDP-AR-HMM inference
+  possibility of lumping together multiple similar, but distinct states. In 
+  Section~\ref{method:realizations}, we explain how we use these 24 independent
+  models in order to generate a single MSD prediction.
 
@@
   a more easily interpretable size 
-  %BJC: added following in response to Chris' below comment. I think I'm interpretting what he's saying right
   % CPC: perhaps keep hammering home not only reducing, but also reemphasize why absolute
   % value of some parameters really not of interest 
-  and because the parameters of a single states does not always give meaningful physical insight. 
-  For each solute studied, we identified approximately 300-500 independent states, 
-  each with separate VAR(1) parameters. Many of these states exhibit very similar
-  dynamical behavior except their mean levels in each dimension are different.
+  %MRS: explain why parameters of single states don't give insight; more context needed?  Is CPC talking about
+  %MRS: some some of the parmameters not being interesting in general, not just the values for some states?
+  and because the parameters of a single state alone does not always have enough context
+  to provide meaningful physical insight. For each solute studied, we identified 
+  approximately 300-500 independent states, each with separate VAR(1) parameters.
+  Many of these states exhibit very similar dynamical behavior except their mean 
+  levels in each dimension are different.
 
@@
   hydrophilic pores to hydrophobic tails. However, the channels are isotropic along
-  the pore axis so we do not cluster in means in the $z$ dimension. Before carrying
+  the pore axis so we do not cluster on the means in the $z$ dimension. Before carrying
   out the agglomerative clustering algorithm, we normalized each clustering dimension
-  by its variance and shifted the mean to zero.
-
-  %BJC: small modifications to this paragraph for clarity
+  by its variance and shifted its mean to zero.
+
   We converted the parameters that are directly related to solute position into 
@@
   $y$ respectively.
-%  rather than $\mu_x$ and $\mu_y$ individually, with the
-%  square $\mu_r$ converting it into the same units as $A$ and $\Sigma$.
-
-  To cluster on $P_{ii}$, we first cast it in terms of the expected dwell times. The expected
+
+  To cluster on $P_{ii}$, we first cast them in terms of the expected dwell times. The expected
   value of the number of sequential self-transitions is simply:
@@
   We obtained estimates of clustered $A$ and $\Sigma$ parameters as well as a
-  single $T$, describing transitions between all possible clustered states exhibited by
-  the ensemble of trajectories, using the inference component of the HDP-AR-HMM
-  algorithm. We applied the HDP-AR-HMM simultaneously on all 24 zeroed solute
-  trajectories with state sequences fixed according to the remapped clustered 
-  state assignments. This is only possible because the state sequence is fixed. 
-  In cases where one does not know the state sequence and would like to 
+  consensus $T$ matrices, describing transitions between all possible clustered states 
+  exhibited by the ensemble of trajectories, using the inference component of 
+  the HDP-AR-HMM algorithm. We applied the HDP-AR-HMM simultaneously to all 24
+  zeroed solute trajectories with state sequences fixed according to the remapped 
+  clustered state assignments. Simultaneous application of the HDP-AR-HMM to 
+  all trajectories as we have done is only possible because the state sequence 
+  is fixed. In cases where one does not know the state sequence and would like to 
   incorporate data from multiple trajectories, one can apply the beta process (BP)
@@
   For both approaches, we drew state sequences with transition probabilities given 
-  % BJC: Chris wasn't clear where T came from for method 2. I tried to make it clearer in 
-  % last paragraph of previous section. Let me know if it's not
   by $T$ of the HDP-AR-HMM. While in a given state, we simulated motion according to the 
@@
   For the MD MSDs, we bootstrapped according to Method 1, sampling with 
-  replacement from the ensemble of 24 solute trajectories.
+  replacement from the single ensemble of 24 solute trajectories.
 
@@
   MSD of the realizations of our models enters a linear regime near a 5 ns time lag
-  (see Figure~\ref{S-fig:MET_nclusters} of the Supporting Information for example).
+  (see Figure~\ref{S-fig:unclustered_msd_shortlag} of the Supporting Information for example).
   Since MSD sampling decreases with increasing time lag, longer trajectory 
-  realizations help to extend the linear region.
-  %BJC: need to confirm these details
-  For all solutes, we generated 200 ensembles of 24 5 $\mu s$ trajectories and 
-  estimated $D$ from the slope fit between 10 ns and 1000 ns. We used weighted 
-  least squares to fit the slope with weights determined by the number of time 
-  lags used to compute the average ($T - \tau$ in equation~\ref{eqn:tamsd}). 
+  realizations help to extend the linear region. For all solutes, we generated
+  200 ensembles of 24 5 $\mu s$ trajectories and estimated $D$ from the slope 
+  fit between 10 ns and 1000 ns. We used weighted least squares to fit the 
+  slope with weights determined by the number of time lags used to compute 
+  the average ($L - \tau$ in Equation~\ref{eqn:tamsd}). 
   We bootstrapped error bars for the final reported selectivities. For each 
@@
   We applied the HDP-AR-HMM independently to all 24 trajectories of each of the four solutes studied.
-  The number of states found for each trajectory varied between 2 and 45.  %BJC4: MET: (5, 28), URE: (5, 45), ACH: (2, 25), GCL: (7, 35)
+  The number of states found for each trajectory varied between 2 and 45.
   Figure~\ref{fig:rz_unclustered} shows the state sequence determined by the HDP-AR-HMM for
@@
 
-  %BJC6: added. Should I add a figure?
   A potential shortcoming of the HDP-AR-HMM applied to MD simulations is its 
@@
   timescales.
-  %BJC6: could hypothesize why using previous work as support
 
@@
   \end{subfigure}
-  \caption{For methanol, ethylene glycol and acetic acid, the MD MSDs (black) and the MSDs
-  calculated from realizations of the HDP-AR-HMM match within uncertainty. The MD MSD of
-  urea is under-predicted by the HDP-AR-HMM.}\label{fig:unclustered_msds}
+  \caption{For methanol, ethylene glycol and acetic acid, the MD MSDs (black) and
+  the MSDs calculated from realizations of the HDP-AR-HMM (orange) match within 
+  uncertainty. The MD MSD of urea is under-predicted by the HDP-AR-HMM.
+  }\label{fig:unclustered_msds}
   \end{figure}
@@
 
+  % BJC: Note that this figure is not finalized. It just takes a while to make 
+  % because of bootstrapping and I keep forgetting to let it run overnight. I 
+  % actually did it once, but had set save=False in the function I used in a jupyter notebook
+  % In its final form, the errorbars will get smaller, and the means don't change by much.
   \begin{figure}
@@
 
-  The data suggests that the particular LLC membrane studied in this work is
-  capable of selectively separating urea and acetic acid from ethylene glycol
-  and methanol. Ethylene glycol and methanol have comparable diffusivities
-  while urea and acetic acid have much lower diffusivities.
-
-  %MRS5: well-written paragraph, tells a convincing story.
+  The data suggests that the particular LLC membrane studied in this work, 
+  up to the resolution of the molecular modeling, is capable of selectively 
+  separating urea and acetic acid from ethylene glycol and methanol. Ethylene 
+  glycol and methanol have comparable diffusivities while urea and acetic 
+  acid have much lower diffusivities.
+
   If we can understand the mechanisms that lead to the various observed transport
@@
   \end{subfigure}
-  %MRS5: should make it clearer these are from the 10 clusters studied earlier. 
-  \caption{(a) Stochastic trajectory realizations generated from our model (blue) based on
-  the 10 clustered methanol parameter sets do not qualitatively reproduce the diversity
-  of behavior seen in our MD trajectories. (b) MSD predictions by clustered parameter sets consistently
-  under-predict the MD MSD. They appear to do a better job of predicting MSDs as the number
+  \caption{(a) Stochastic trajectory realizations generated from our model 
+  (blue) based on the 10 clustered methanol parameter sets do not qualitatively
+  reproduce the diversity of behavior seen in our MD trajectories (black). 
+  (b) MSD predictions by clustered parameter sets consistently under-predict 
+  the MD MSD. They appear to do a better job of predicting MSDs as the number
   of clusters increases.}\label{fig:clustered_dynamics}
@@
   trajectories (States 1--5). Although a majority of the solutes visit these 5 
-  dominant states, the amount of time spent in each varies widely. For example, methanol
+  predominant states, the amount of time spent in each varies widely. For example, methanol
   does not spend a significant amount of time in State 3 because, as discussed later, it 
-  is a short-lived state. We still consider State 3 as a dominant state because it
+  is a short-lived state. We still consider State 3 as a predominant state because it
   is may be a significant contributer to solute MSD.
-  %MRS5: maybe explicitly indicate the 5 stattes?  I only see four red bars with appreciable sampling.
-  % The solutes spend varying amounts of time in each of these states.
-  %BJC6: I'm focusing on the blue bars. It's a hopping state so not much time is spent there,
-  % but most of the solutes still show that behavior. Added a couple sentences to clarify
   }
@@
 
-  The parameters of the five dominant states provide clues about the associated solute
+  The parameters of the five predominant states provide clues about the associated solute
   behavior. Characteristic dynamics of the following states appear in 
@@
   \begin{enumerate}[label={State \theenumi :}, leftmargin=3.5\parindent]
+
      \item This state has intermediate dwell times with high past-hop dependence (high
@@
      distances from the pore center.
+
      \item This state's radial mean of 2.4 nm implies that it occurs exclusively in the
-     tail region based. Its fluctuations are small and there is little past hop dependence.
+     tail region. Its fluctuations are small and there is little past hop dependence.
+
      \item This is likely a hopping state that strongly contributes to the solute's MSD. 
@@
      Like State 1, we see this type of behavior near the pore center and near the ends of the tails.
-     \item This is a trapping state, having the longest expected dwell time among the dominant
+
+     \item This is a trapping state, having the longest expected dwell time among the predominant
      states, with a strong dependence on its previous fluctuation. Evidence from 
-     Figure~\ref{fig:clustered_traj_MET} and a radial mean of 1.8 suggest that it tends to
-     occur at intermediate distances from the pore center with perhaps a higher tendency
-     to occur deeper within the tails.
+     Figure~\ref{fig:clustered_traj_MET} and a radial mean of 1.8 nm suggest that 
+     it tends to occur at intermediate distances from the pore center with perhaps
+     a higher tendency to occur deeper within the tails.
+
      \item This is an intermediate-length trapping state that occurs 0.9 nm from the pore 
-     center on average. It's fluctuations are tight and relatively independent of its previous 
+     center on average. Fluctuations are small and relatively independent of its previous 
      fluctuation.
+
   \end{enumerate}
 
-  \textit{Relating Parameters to Solute-Membrane Interactions}: Based on the molecules
-  and ions which constitute this system, it is logical to search for hydrogen bonding
-  interactions and solute association with sodium ions. All of the solutes are
-  polar and have hydrogen bond donating and accepting groups. The monomers 
+  \textit{Relating Parameters to Solute-Membrane Interactions}: Based on the
+  molecules and ions which constitute this system, it is logical to search for hydrogen 
+  bonding interactions and electrostatic association with sodium ions. All of 
+  the solutes are polar and have hydrogen bond donating and accepting groups. The monomers 
   have 10 oxygen atoms distributed from head to tail that are capable of 
@@
 
-  For methanol, hydrogen bonding is a much more dominant interaction than sodium
-  ion association. In Figure~\ref{fig:hbond_fractions}, we show that methanol 
+  For methanol, hydrogen bonding is a much more dominant interaction than association
+  with sodium ions. In Figure~\ref{fig:hbond_fractions}, we show that methanol 
   participates in hydrogen bonds to various parts of the monomer between 27 and
-  45\% of the total time it occupies the dominant states. Methanol associates 
-  with sodium ions less than 10\% of the time in dominant states.
+  45\% of the total time it occupies the predominant states. Methanol associates 
+  with sodium ions less than 10\% of its time and for relatively short periods 
+  of time while in predominant states.
 
   The distribution of types of hydrogen bonds and associated hydrogen bond lifetimes
-  varies by dominant state. States 1 and 2 are dominated by hydrogen bonds to the 
-  head groups and, to a smaller extent, the ether linkages. State 1 methanol
-  molecules that donate hydrogen bonds to the tail oxygen atoms exhibit by far 
-  the longest hydrogen bond lifetimes among all states. States 3 and 4 hydrogen 
-  bond to all regions of the monomer relatively evenly, which is consistent with
-  our earlier observation that states 3 and 4 are representative of behavior 
-  seen radially throughout the membrane pores. State 3 has the lowest hydrogen 
-  bond and sodium association lifetimes which is consistent with its short dwell
-  times. These are fleeting interactions since it is likely a high variance 
-  transitory state.
-  %MRS5: not clear what a ``jumping state'' is.
-  %BJC6: tried to be more precise. changed to 'high variance transitory state'
-  Methanol molecules in state 5 hydrogen bond almost exclusively to the carboxylate
-  head groups and ether linkages which is consistent with the radial mean of the
+  varies by predominant state. States 1 and 2 are dominated by hydrogen bonds to the 
+  ester groups at the ends of the monomer tails and, to a smaller extent, the ether 
+  linkages between the monomer head group and tails. State 1 methanol molecules that
+  donate hydrogen bonds to the tail oxygen atoms exhibit by far the longest hydrogen
+  bond lifetimes among all states. Methanol molecules in states 3 and 4 hydrogen 
+  bond to all regions of the monomer relatively evenly, which is consistent with our earlier observation that
+  states 3 and 4 are representative of behavior seen radially throughout the membrane
+  pores. State 3 has the lowest hydrogen bond and sodium association lifetimes which
+  is consistent with its short dwell times. These are fleeting interactions since it
+  is likely a high variance transitory state. Finally, methanol molecules in state 5
+  hydrogen bond almost exclusively to the carboxylate head groups and ether linkages 
+  which is consistent with the low (close to the pore center) radial mean of the 
   cluster.
@@
   \end{subfigure}
-  % BJC4: I put this one here for compact-ness. Not sure if I should separate into own figure
   \begin{subfigure}{0.475\textwidth}
@@
   \end{subfigure}
-  %MRS5: specifically mention at the beginning which solute.
   \caption{(a) We analyzed hydrogen bonds donated by methanol to the highlighted oxygen
   atoms in three regions of the monomer: the carboxylate groups (blue), the ether linkages
-  (green) and the tails (red). (b) For each dominant state (States 1--5 described in 
-  Figure~\ref{fig:prevalence}, we plotted the fraction of the total time in that state 
+  (green) and the tails (red). (b) For each predominant state (states 1--5 described in 
+  Figure~\ref{fig:prevalence}), we plotted the fraction of the total time in that state 
   spent hydrogen bonding to various regions of the monomer, color coded to match (a).
-  (c) For each type of hydrogen bond in each dominant state, we calculated the 95th percentile
+  (c) For each type of hydrogen bond in each predominant state, we calculated the 95th percentile
   of hydrogen bond lifetimes. (d) We also analyzed the frequency and lifetimes of solute 
   association with sodium ions. Methanol associates with sodium less than 10\% of the total 
-  time it occupies any of the dominant state.
+  time it occupies any of the predominant states.
   }
@@
   solutes in this study and learn new information by comparing their behavior. 
+  Where referenced in the following analysis, we define the predominant states 
+  exhibited by each solute as any state visited by at least half (12) of the 
+  solute trajectories. By our definition and based on our choice to study 10 
+  clusters for each solute, methanol, ethylene glycol, urea and acetic acid are
+  characterized by 5, 6, 5 and 4 predominant states respectively 
+  (see Figure~\ref{S-fig:state_prevalence} of the Supporting Information).
 
@@
   In our previous work, we showed that sodium ions frequently associate with the 
-  carbonyl groups of acetic acid and urea.
+  carbonyl groups of acetic acid and urea because the carbonyl oxygen atoms are
+  unshielded and have a relatively high partial negative charge.~\cite{coscia_chemically_2019}
 
@@
   their time close to the pore center. Only methanol has a significant density
-  far from the pore center. (c) The largest expected value (see 
-  Equation~\ref{eqn:dwell_times}) of dwell times among the dominant clustered 
-  states for each solute are inversely related to the solute's MSD. 
-  % BJC: Copying Chris' comments below:
-  % CPC: Discussion is confusing. guessing error bars are from measured simulation 
-  % dwell times in dominant state.  
-  % BJC: will add error bar explanation once I figure out exactly how to modify the figure
-  % CPC: what if trajectory has more than one dominant state? (seems from fig like 
-  % you take one with largest dwell time from your model. 
-  % BJC: All solutes have at  least 4 dominant states by my definition. maybe it would 
-  % be better to sample dwell times from all of the dominant states. Just weight 
-  % their contributions. Not sure if weighting should be with respect to the fraction
-  % the total simulation time spent in each state, or the number of times the state
-  % was visited.
-  % CPC: might want to better connect MSDs of model in fig.3 to fig 9 c and 
-  % expand/clarify discussion on connection of fig 9c to other panels just lots
-  % of ambiguity here, but results seem promising.
-  % BJC: is it worth plotting bars with the MSD after 1000 ns as part of (c)? 
-  %MRS5: not clear what ``largest expected'' means here.
-  %BJC6: modified to 'expected value' and referenced equation   
-  (d) The expected dwell time of solutes increases 
-  in states with high local number density of surrounding heavy atoms.
+  far from the pore center. (c) The 95\textsuperscript{th} percentile of dwell
+  times, collected by measuring the length of each disjoint segment according 
+  to the clustered state sequences, is inversely related to the solute MSDs
+  after a 1000 ns time lag.
+  (d) The expected dwell time of solutes increases in states with high local 
+  number density of surrounding heavy atoms.
   }\label{fig:summaries}
@@
 
-  % BJC: Chris was confused by this paragraph
-  Solutes with dominant states characterized by long dwell times tend to 
-  have lower MSDs. We define the dominant states exhibited by each solute
-  as any state visited by at least half (12) of the solute trajectories.
-  By our definition and based on our choice to study 10 clusters for each 
-  solute, methanol, ethylene glycol, urea and acetic acid are characterized
-  %BJC: added this supporting figure 
-  by 5, 6, 5 and 4 dominant states respectively (see Figure~\ref{fig:state_prevalence}
-  of the Supporting Information). In Figure~\ref{fig:dwell_time_summary}, we
-  plot the expected dwell time of each solute in the dominant state which 
-  has the the highest self-transition probability. The MSDs shown in 
-  Figure~\ref{fig:unclustered_msds} are inversely related to the maximum 
-  expected dwell times. Both acetic acid and urea participate in many hydrogen
-  bonds and sodium ion association interactions and the states visited by both 
-  solutes have similar distributions of radial means, however acetic acid is 
-  subject to much longer dwell times, and hence a lower MSD. This may be 
-  because acetic acid is a stronger hydrogen bond donor than urea.
+  Solutes which experience longer dwell times tend to have lower MSDs. 
+  In Figure~\ref{fig:dwell_time_summary}, we plot the 95\textsuperscript{th}
+  percentile of dwell times for each solute. The evidence suggests that the 
+  long time scale MSDs (we use the MSDs after a 1000 ns time lag in Figure~\ref{fig:dwell_time_summary})
+  are inversely related to dwell times. Both acetic acid and urea participate 
+  in many hydrogen bonds and sodium ion association interactions and the states
+  visited by both solutes have similar distributions of radial means, however
+  acetic acid is subject to much longer dwell times, and hence a lower MSD. 
+  This may be because acetic acid is a stronger hydrogen bond donor than urea.
 
@@
   of solute entrapment. In Figure~\ref{fig:density_comparison}, we show that the
-  expected dwell time of solutes in dominant states tends to increase with 
-  local density. High local density combined with polar and electrostatic interactions
-  act cooperatively to keep solutes in place.
+  expected dwell time (see Equation~\ref{eqn:dwell_times}) of solutes in 
+  predominant states tends to increase with the local density of surrounding 
+  heavy atoms. High local density combined with polar and electrostatic 
+  interactions act cooperatively to keep solutes in place.
 
@@
   By pooling MSDs predicted by models fit to each trajectory, we can reproduce
-  the solute MSDs measured directly from the our MD-simulated trajectories. 
+  the solute MSDs measured directly from our MD-simulated trajectories. 
   The low computational expense of generating these stochastic trajectories allows
@@
   Detailed explanations and expansions upon the results and procedures mentioned in
-  the main text are described in the Supporting Information. 
-  %This information is
-  %available free of charge via the Internet at http://pubs.acs.org.
+  the main text are available in the Supporting Information.
 

### 2020-06-01 Ben_Manuscripts/hdphmm/Draft.tex
added TOC graphic
comments

@@
   multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
-
+  %MRS: citation missing for coscia_chemically_2019
   We have already advanced our understanding of LLC monomer design in our previous work
@@
   states, thus allowing the model's complexity to be driven by the complexity
-  of the data.~\cite{teh_hierarchical_2006} We will refer a model calibrated with
+  of the data.~\cite{teh_hierarchical_2006} We will refer to a model calibrated with
   this type of prior as an HDP-HMM; this model class is sometimes referred to
@@
   within a fixed state.~\cite{calderon_data-driven_2014}
-  Fox et al. formulated a method that accounts for temporal dependence betwee
+  Fox et al. formulated a method that accounts for temporal dependence between
   successive observations by incorporating Markov jump linear systems (MJLSs)
@@
   improved predictive models. We cluster the parameters of individual states
-  in order to reduce the total state space down to an interpretable size
+  in order to reduce the total state space down to an interpretable size.
   This allows us to learn the implied dominant physical mechanisms and describe
@@
   efficiently uncover underlying transport mechanisms which give rise to different 
-  solute dynamical behavior. We cluster similar state parameters across all
-  trajectories in order to reduce the total state space and to understand which
+  solute dynamical behavior. We cluster 
+  %MRS:
+  %similar state parameters 
+  states with similar parameters
+  across all
+  trajectories in order to reduce the total state space and to 
+  %MRS:
+  identify
+  %understand 
+  which
   segments of the solute trajectories exhibit similar behavior. We use the 
@@
   occupy the tail region with the rest are near the pore center.~\cite{coscia_chemically_2019}
+  %MRS: fix citation above.
 
@@
   in order to encourage higher self-transition probabilities since we physically expect
+  %MRS: maybe ``physically observe?'' instead of physically expect.
   solutes to stay trapped in states for appreciable amounts of time.
@@
   %MRS: explain why parameters of single states don't give insight; more context needed?  Is CPC talking about
-  %MRS: some some of the parmameters not being interesting in general, not just the values for some states?
+  %MRS: some some of the parameters not being interesting in general, not just the values for some states?
   and because the parameters of a single state alone does not always have enough context
@@
   We obtained estimates of clustered $A$ and $\Sigma$ parameters as well as a
+  %MRS: check again agreement on $T$ and $P$ - you switched to $P$, right? Or are they 2 different things?
   consensus $T$ matrices, describing transitions between all possible clustered states 
+  %MRS: do you explicitly say how to get the consensus transition matrices?
   exhibited by the ensemble of trajectories, using the inference component of 
@@
   method of trajectory generation:
+  %MRS: this is a bit confusing.  Is there an expectation these should give consistent parameters?
+  %MRS: the second is boostrapping an MSD over 1000 trajectories, and the first is boostrapping an MSD over 24 trajectories.
+  %MRS: these should have different amounts of noise, making them hard to compare? Is this an issue?
   \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
@@
   \includegraphics[width=0.6\textwidth]{selectivity.pdf}
-  \caption{Of the solutes studied, the current generation of H\textsubscript{II}
+  \caption{Of the solutes studied, 
+  %MRS: add qualifier.
+  the models predict that 
+  the current generation of H\textsubscript{II}
   LLC membranes may have the most success selectively removing acetic acid and,
@@
 
-     \item This state has intermediate dwell times with high past-hop dependence (high
+     \item This state has intermediate dwell times with high past-hop dependence (large
      entries of $A$). The cluster's radial mean is 1.5 nm which is about halfway between
@@
 
-  %\newpage
-
-  %\section*{TOC Graphic}
+  \newpage
+
+  \section*{TOC Graphic}
+
+  \begin{figure}[!htb]
+  \centering
+  \includegraphics[width=3.25in]{hdphmm_TOC.pdf}
+  \end{figure}
 
@@
 % LocalWords:  functionalized teuerle jasra markov bioinformatics hughes yoon
-% LocalWords:  hines diarization MJLSs MJLS SLDSs SLDS hamada jk params MNIW
+% LocalWords:  hines diarization MJLSs MJLS SLDSs SLDS hamada jk params MNIW BP
 % LocalWords:  plateaued nclusters leftmargin trans diffusivity sorption alkane
 % LocalWords:  ness substituents desalination fonseca couto welch singhal noe
-% LocalWords:  shirtsgroup superdiffusive diffusivities
+% LocalWords:  shirtsgroup superdiffusive diffusivities jazani wang persson CPC
+% LocalWords:  shortlag jupyter ester

### 2020-06-01 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{xr}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{scrextend}

\externaldocument[S-]{Supporting_Information}
\externaldocument[M-]{Final_Draft}

\begin{document}

\graphicspath{{./figures/}}

\begin{center}
\textbf{Response to reviewers: Capturing Subdiffusive Solute Dynamics and Predicting
Selectivity in Nanoscale Pores with Time Series Modeling} \\
Authors: Benjamin J. Coscia and Michael R. Shirts
\end{center}

We thank the reviewers for carefully reading over our manuscript and providing
helpful comments. We have taken the suggestions into consideration and made
appropriate revisions to the manuscript document. The comments have been reproduced
in italics and all changes to the text have been documented below. In cases where 
we modified the text we included the original text (denoted by ``Original text:") 
followed by the new text (denoted by ``New text:").

\section*{Response to Reviewer 1}

\begin{enumerate}[label={Comment \theenumi :}, leftmargin=3.9\parindent]

  \item \textit{\textbf{Page 5 line 19:} In this work, we use the output of our MD simulations
        to construct \textbf{two classes} of mathematical models which aim to predict membrane 
        performance while providing quantitative mechanistic insights. \\
        \textbf{Page 5 line 47:} We treat our system in terms of \textbf{two well-known} classes of 
        anomalous subdiffusion: \textbf{fractional Brownian motion} (FBM) subordinate to a 
        \textbf{continuous time random walk (CTRW)}, or subordinated FBM (sFBM) for short. \\ \\
        I am a little confused by these sentences, does the two well-known classes correspond to FBM
        and CTRW, or refer to different classes of modeling approaches used later in the manuscript?}

  %BJC: use a different word?

  Author reply: We thank the reviewer for identifying our potentially confusing choice of words.
  The first sentence (Page 5 line 19) refers more broadly to the two types of stochastic models 
  formulated in this work: the Anomalous Diffusion model and the Markov state-dependent dynamical
  model. The second quoted sentence (Page 5 line 47) refers to the different types of
  motion (FBM and CTRW) that give rise to anomalous diffusion specifically. The paragraph expands
  upon the introduction given in the previous paragraph. We have modified the second quoted 
  sentence as follows to remove ambiguity.

  Original text:
  \begin{quote}
  We treat our system in terms of two well-known classes of anomalous subdiffusion: 
  \end{quote}

  New text:
  \begin{quote}
  In this first approach, we treat our system in terms of two well-known types of molecular
  motion that leads to anomalous subdiffusion: 
  \end{quote}

  \item \textit{\textbf{MD-section} \\
        \textbf{Page 8 and 9} \\
        The authors refer to ref 13 (where these simulations have been performed before), 
        nevertheless I find that the MD section does not provide sufficient amount of details 
        to be self-contained. Could the authors specify the force field, as well as summarize 
        its reliability for this particular system (often simulations involving changed solutes
        through pores require polarizable force fields)? Next, reading this section I would 
        also like to know how well finite size effects are controlled for with this specific 
        membrane and these specific solutes. Lastly, it would be natural to report the size 
        of the system in this section (I found it eventually in the introduction after 
        searching for it throughout the manuscript).}

  Author reply: We thank the reviewer for pushing us to include more details about our 
  molecular simulations in order to boost reproducibility. The length of the manuscript made
  us wary to include information that could be accessed elsewhere, however there are 
  benefits to keep this very important section self-contained.

  We added the following text in order to inform the reader of the system's size:

  New text:
  \begin{quote}
  Each unit cell is contained $\sim$ 62,000 total atoms. % BJC: do you think he want unit cell dimensions? X x Y x Z? 
  \end{quote}

  We added the following text to address comments related to our choice of force field:

  New text:
  \begin{quote}
  We parameterized monomers and solutes using the Generalized Amber Force Field (GAFF) and
  water molecules using the TIP3P water model.~\cite{} We made each choice in order to
  ensure that our approach is accessible and reproducible for a wide audience and so that
  it is easy to study a broad range of solutes and monomer chemistries in high throughput. 
  The main goal of this work is to develop stochastic models which can reproduce solute
  behavior on MD time scales regardless of the force field. In future work, it may be 
  beneficial to employ specialized force fields, like polarizable force fields in 
  order to improve the accuracy of selectivity predictions.
  \end{quote}

  %BJC: not sure if anything should be added to text
  %BJC: I could use some help on justification
  With respect to finite size effects, we have not made any explicit corrections, but
  feel they are not of great concern for this work. While the tails of the monomers from
  different pores interact across periodic boundaries, we are not interested in their
  diffusion. In our previous work, we have shown that monomer motion is negligible on 
  simulation time scales. Our main focus is on the time series of the solutes in the \
  membrane pores. On the 5 $\mu s$ time scales which we simulate we do not see any 
  solutes cross between pores. Therefore, we expect similar solute behavior in larger
  arrays of pores. A study of finite size effects may be interesting in future work, but
  we do not feel it is justified for this study given the computational cost of studying
  larger systems. We also believe it would have little influence on the way in which 
  we fit our models to the time series.

  % BJC: easy to specify force field.
  % BJC: what to say about polarizable force fields? Focus on methods? Maybe throw in some 
  % references to solute transport with polarizable force fields?
  % finite size effects -- ?? sufficiently long pores in z?
  % BJC: no gaurantee polarizable would be good since there aren't any out of the box 
  % polarizable force fields

  \item \textit{\textbf{Figure 5 page 25:} \\
		First, the symbols within the figure are very small and barely readable, and probably not
		according to authors guidelines for figures. Second, the caption, as with the other captions of
		this manuscript, contain a lot of interpretation that normally are placed in the main text. This
		might be a particular style of the authors that has its benefits, however in this specific case the
		caption fails at explaining what exactly this figure is showing. The way I interpret this figure is:
		the symbol on the y-axis marks a general parameter and the boldface symbol marks the
		parameter shown in the histogram. Am I correct? If so, I would strongly recommend modifying
		y-axis and the caption to make this clear.}

		Author reply:
		%BJC: modify figures
		%BJC: cut down on interpretation in all figures

  \item \textit{\textbf{Page 6 line 55}: The second measure of success is based on the qualitative
        comparison between individual realizations of solute trajectories generated ...\\ \\
		Here I am a little curious. Are there no measures which can be used to quantify the similarity of
		the trajectories, such as autocorrelation functions etc, or are such measures inputs for the
		parametrization of the model which cannot be used?}

		Author reply: In short, we do not believe there are any other suitable methods for comparing
		similarity beyond the checks which we show in this work. Autocorrelation is indeed an input 
		to the anomalous diffusion and Markov state-dependent dynamical model, specifically through
		the Hurst parameter which is generated by fitting to autocorrelation of solute jumps. The
		anomalous diffusion model is only parameterized by the distribution of hop length, the 
		distribution of dwell times and the degree of autocorrelation between hops, all of which
		are measured directly from MD. It may be possible to think of other metrics of success
		for the Markov state-dependent dynamical model, but it fails the qualitative test and
		thus does not merit any further checks.

  \item \textit{One question that came to mind reading the paper was: why is the model only in 
  		one dimension and not two (for example using cylindrical coordinates)?}

  		Author reply: We thank the reviewer for their sensible question. The simplest answer
  		to this is that ultimately we are only concerned with transport along the pore axis. Radial
  		solute transport (with respect to the pore center) is effectively bounded and only 
  		contributes to axial MSD to the extent that it influences axial transport. We 
  		do acknowledge that the radial location of solutes has an influence on solute
  		hopping behavior which is why attempted to create the two mode anomalous diffusion model.
		From a more mathematical standpoint, there are two factors which pose challenges with
		increasing dimensionality. First, we have a relatively low amount of data, and therefore
		it is challenging to adequately parameterize behavior as a continuous function of both 
		$r$ and $z$. Second, it is not trivial to simulate fractional motion in multiple dimensions.
		We were fortunate to find an efficient python implementation of FBM and we needed to
		develop our own approximation of 1D fractional L\'{e}vy motion based on literature. 
		We felt there was little to gain by models more complicated than those showcased in our
		work.

		However, we would like to acknowledge that we have a strong desire to incorporate data
		from multiple dimensions. We are actively investigating a new modeling approach which 
		allows us to overcome these issues and to use cylindrical representations with ease.

  \item \textit{\textbf{Page 35 line 12-14}: \\
   		We do not consider the two mode AD model because it has a broken correlation structure \\ \\
        I was a little disappointed to see only the single mode being used. Could the authors 
        elaborate on this point? Exactly how does this broken correlation structure hinder such
        an investigation?}

        Author reply: We are pleased with the reviewer's interest in the two-mode model. While it
        would be technically simple to apply the same mathematical framework to study the long time
        scale performance of the two-mode model, we feel it may be misleading to the reader.
        As described in the text, the predicted MSDs of the two-mode model may indeed show better 
        qualitative behavior than the one-mode model. Specifically, the two-mode model becomes
        linear on long timescales which may be more consistent with our MD results. However, this 
        long time scale linear behavior of the two-mode model has only a mathematical basis and
        no physical basis. As discussed in the text, the one-mode model has persistent curvature
        since hop correlation persists indefinitely for fractional motion. However, for the two-mode
        model, each time a solute transitions between the pore and tail regions, we must generate a
        new FBM process because we lack a proven technique for simulating fractional 
        motion that incorporates time-dependent variation in the width of the hop length 
        distributions.

        Perhaps, most importantly, Section 3.3 is primarily used to demonstrate our mathematical
        framework. Applying it to the two mode model would be trivial. We chose to use the one-mode 
        model to demonstrate because it passes our qualitative and quantitative checks and is
        mathematically sound. As the reviewer points out, it is likely that our approach to 
        modeling the solute time series is not yet suitable to make quantitative predictions of 
        flux and selectivity. But our approach opens the door for applying the same analysis to 
        improved time series modeling techniques.

  \item \textit{\textbf{Page 35 line 20-42:}\\
        A pore-length of 50 nm is a little underwhelming compared to 7 micrometers. Reading the paper
		I do not understand what lies behind this limitation - what hinders the sampling one really would
		like to have when doing such modeling? Also, you write about RAM-requirements scaling more
		than linearly (assuming with L). What exactly lies behind this scaling? Finally, just out of
		curiosity, are there ways of coarse-graining/renormalizing the random walk such that larger time
		and length scales can be reached? That being said, I am impressed by fit against the scaling
	  	law.}

	  	Author reply: We can appreciate why the reviewer has questioned this limitation.
		When simulating fractional motion, each step must be correlated to all of its previous 
		steps. Therefore the computational cost increases with each added step. We show in the paper
		that the mean first passage time across the pores scales with L$^{\alpha}$, and $\alpha$ is
		always $\geq$ 2. As the degree of anti-correlation between hops increases, the scaling
		parameter also increases. Therefore, we need to generate very long trajectories, with 
		correlation between all data points, in order to sufficiently sample the MFPT distribution 
		before fitting them to Equation 9. This is especially challenging with slow-moving solutes
		like acetic acid. We needed to simulate over 2 million timesteps in order to sufficiently
		sample the MFPT over a 50 nm pore. This procedure becomes computationally expensive very
		quickly, and requires ample RAM to store the trajectories as they constructed.

		Given the quality of our fits in Figure 11b, we felt it was not necessary to carry out the
		calculation for longer pores which would likely offer little extra benefit to the insight we
		already gained.

	  	This may be an issue that could be overcome by developing specialized algorithms and perhaps 
	  	by using a compiled computer language like C++.

	  	%BJC: Could reasonably go beyond 50 nm but 7 microns becomes tough
	  	%BJC: building in the correlation structure is computationally expensive. Reference a paper describing how FBM is simulated
	  	%BJC: could benefit from optimized libraries, but python isn't fast enough
	  	%BJC: also need to specify the number of steps to take beforehand
	  	%BJC: truncated correlation functions may allow us to surpass the limitation

  \item \textit{In this paper the models are only evaluated by their ability of achieving 
		  self-consistency with the trajectories used as input. This is conceptually not ideal. 
		  Are there no experimental data or mathematical models which act as a reference for 
		  the models? Please elaborate.}

		  Author reply:
		  % BJC: maybe just give some background on this project overall. Could add a paragraph
		  % to explain this

  \end{enumerate}

\noindent Optional comment to consider:\\
\begin{addmargin}[5.8em]{0em}
	\textit{Having read the paper thoroughly twice, I still struggle with the acronyms of the different random
	walks. Given that this is not a journal of stochastic processes, it is my opinion that the readability
	and accessibility of the manuscript would be greatly improved by writing the full names of the
	random walks in the text while keeping acronyms in figures. \\}

    %BJC: I have no problem with this

\end{addmargin}

\noindent Small typos to consider: \\
\begin{addmargin}[3.3em]{0em}
\begin{itemize}
  \item \textit{Micro in micrometer should be written with upright Greek letter.} \\ \\
  		Author reply:

  \item \textit{d as “dt” in integrals should be non italic.} \\ \\
  		Author reply:

  \item \textit{Page 10 line 28: T should be in symbol form.} \\ \\
  		Author reply:

  \item \textit{Symbol T is used for both time and transition matrix, perhaps use some matrix notation.} \\ \\
  		Author reply:

  \item \textit{The references should be checked thoroughly by the authors. Ref 13, which is arguably
  the most important reference for this paper is missing the volume number.} \\ \\
		Author reply:
\end{itemize}
\end{addmargin}

\section*{Response to Reviewer 2}

\begin{enumerate}[label={Comment \theenumi :}, leftmargin=3.9\parindent]

    \item \textit{ Abstract: here it is difficult to understand what is meant with "dwell times, hop 
    lengths between dwells and correlation between hops", without reading the whole Introduction (and 
    possibly reference 13, which by the way is not completely listed in the References section). The 
    authors should briefly describe the complex transport behavior observed in their previous study of
    these systems (for example, by including information from the Introduction, i.e., the last paragraph
    of page 3 and first paragraph of page 4).}

    Author reply:

    \item \textit{Some of the acronyms were not defined (or perhaps I missed them), for example 'AD' 
    (page 7) and 'MLE' (page 11)}

    Author reply:

    \item \textit{In the Introduction, specifically the last paragraph of page 3 and first paragraph
    of page 4, the authors should refer to Figure 1 to complement their description of the complex solute
    dynamics.}

    Author reply:

    \item \textit{Caption of Figure 7 should refer the reader to Table 2 for completeness}

    Author reply:

\end{enumerate}

%\bibliographystyle{ieeetr}
%\bibliography{transport}

\end{document}

### 2020-06-01 Ben_Manuscripts/hdphmm/Draft.tex
Comments on draft.

@@
      It is short lived and has large fluctuations which often results in very large hops.
-     Like State 1, we see this type of behavior near the pore center and near the ends of the tails.
+     Like state 1, we see this type of behavior near the pore center and near the ends of the tails.
 
@@
   The distribution of types of hydrogen bonds and associated hydrogen bond lifetimes
-  varies by predominant state. States 1 and 2 are dominated by hydrogen bonds to the 
+  varies by predominant state, as seen in more detail in Figure~\ref{fig:hydrogen_bonding}.
+  %MRS: what do you think about this? It maks it easier to read.
+  \begin{itemize}
+  \item States 1 and 2 primarily have hydrogen bonds to the 
   ester groups at the ends of the monomer tails and, to a smaller extent, the ether 
-  linkages between the monomer head group and tails. State 1 methanol molecules that
+  linkages between the monomer head group and tails. 
+  \item State 1 methanol molecules that
   donate hydrogen bonds to the tail oxygen atoms exhibit by far the longest hydrogen
-  bond lifetimes among all states. Methanol molecules in states 3 and 4 hydrogen 
+  bond lifetimes among all states. 
+  \item Methanol molecules in states 3 and 4 hydrogen 
   bond to all regions of the monomer relatively evenly, which is consistent with our earlier observation that
   states 3 and 4 are representative of behavior seen radially throughout the membrane
-  pores. State 3 has the lowest hydrogen bond and sodium association lifetimes which
+  pores. 
+  \item State 3 has the lowest hydrogen bond and sodium association lifetimes which
   is consistent with its short dwell times. These are fleeting interactions since it
-  is likely a high variance transitory state. Finally, methanol molecules in state 5
+  is likely a high variance transitory state. 
+  \item Finally, methanol molecules in state 5
   hydrogen bond almost exclusively to the carboxylate head groups and ether linkages 
@@
   cluster.
+  \end{itemize}
 
@@
   The size and chemical functionality of the solutes dictates the interactions which
-  influence solute transport. In Figure~\ref{fig:hbonds_assoc_summary}, we show that the
+  influence solute transport. Figure~\ref{fig:hbonds_assoc_summary} shows that the
   solutes donate hydrogen bonds and associate with sodium ions to varying degrees.
-  In fact methanol, by far, interacts the least by these mechanisms. This is likely 
+  In fact methanol interacts the least by these mechanisms by far. This is likely 
   because methanol is very small and it is easier for it to partition into the tail
@@
   to different degrees. Sometimes, they participate in both interactions at
-  once. (b) We histogrammed the radial means of the unclustered states weighted
+  once. (b) The radial means of the unclustered states weighted
   by the length of time spent in that state. Most solutes spend the majority of
@@
   times, collected by measuring the length of each disjoint segment according 
-  to the clustered state sequences, is inversely related to the solute MSDs
-  after a 1000 ns time lag.
+  to the clustered state sequences, is inversely related to the solute MSDs.
+  %MRS: this can be explained in the text.
+  %after a 1000 ns time lag.
   (d) The expected dwell time of solutes increases in states with high local 
@@
   in many hydrogen bonds and sodium ion association interactions and the states
-  visited by both solutes have similar distributions of radial means, however
-  acetic acid is subject to much longer dwell times, and hence a lower MSD. 
+  visited by both solutes have similar distributions of radial means, but
+  acetic acid has much longer dwell times, and hence a lower MSD. 
   This may be because acetic acid is a stronger hydrogen bond donor than urea.

### 2020-06-01 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Incorporate Chris' suggestions
comments on supporting.

@@
   The state sequence appears to converge within 500--1000 IHMM iterations. To
-  be sure, we ran 2000 iterations of the IHMM algorithm in order to arrive at a 
+  be certain, we ran 2000 iterations of the IHMM algorithm in order to arrive at a 
   finalized state sequence. Stabilization of the VAR parameters indicates 
@@
   guess at the initial state sequence. (d) A better initial state segmentation
-  via seeding, gives more reasonable estimates of the final state sequence
+  via seeding gives more reasonable estimates of the final state sequence
   as illustrated in Figure~\ref{fig:seed_sequence}.}\label{fig:improvement_state_sequence}
@@
   data. In Figure~\ref{fig:rspread}, we show that `ward' linkage results in 
-  the highest spread in the radials means of the clusters across a range of
+  the highest spread in the radial means of the clusters across a range of
   4--30 total clusters. For a low to intermediate number of clusters, the 
@@
 
-  We use the Silhouette score in order to aid us in choosing the total number of
-  clusters. In Figure~\ref{fig:silhouette_MET}, we plot the Silhouette score as
+  We use the silhouette score in order to aid us in choosing the total number of
+  clusters. In Figure~\ref{fig:silhouette_MET}, we plot the silhouette score as
   a function of the total number of clusters using the `ward' linkage criteria. 
-  A Silhouette score of 1 indicates the best clustering possible, values near
+  A wilhouette score of 1 indicates the best clustering possible, values near
   0 indicate overlapping clusters, and negative values indicate that samples belong to
-  the wrong clusters. For the methanol parameters, the Silhouette score drops off
+  the wrong clusters. For the methanol parameters, the silhouette score drops off
   quickly with number of clusters before plateauing around 7 total clusters. 
@@
   number of clusters as compared to other linkage criteria. (b) The 
-  Silhouette score, used to evaluate the quality of clustering with the 
+  silhouette score, used to evaluate the quality of clustering with the 
   `ward' distance criteria drops precipitously as a function of the chosen
@@
   We incorporate qualitative feedback into the decision on the number of 
-  clusters. Despite its high Silhouette score, Figure~\ref{fig:4cluster_state_sequence}
+  clusters. Despite its high silhouette score, Figure~\ref{fig:4cluster_state_sequence}
   illustrates that using 4 clusters clearly does not distinguish dynamical 
@@
   \end{subfigure}
-  \caption{Although the Silhouette score for four total clusters is high, we do
+  \caption{Although the silhouette score for four total clusters is high, we do
   not see adequate distinction between clusters until we group the parameters
@@
   leading to a high MSD. The parabolic trajectory of the MD MSD curve implies
-  underlying superdiffusion which would require some kind of facilitating
+  underlying super-diffusion which would require some kind of facilitating
   driving force. It is likely that running the trajectory longer would reduce
@@
   The HDP-AR-HMM simulation appears to over-estimate the variance because the actual 
-  distribution of solute fluctuations has heavy tails with a smaller variance (Figure~\ref{fig:emission_widths}).
+  distribution of solute fluctuations has 
+  %MRS: heavy tails should mean larger variance? Clarify?
+  heavy tails with a smaller variance (Figure~\ref{fig:emission_widths}).
   The total distribution of hops is expected to be heavy tailed because it is a
@@
   faithful to MD would use an autoregressive model with L\'evy stable noise. However,
-  this would be less computationally efficient due to lack of conjugate priors.
+  this would be less computationally feasible due to lack of conjugate priors.
 
@@
   number density into number densities measured from instances when the state is occupied 
-  for long (orange) versus short(red) dwell time states. We define define `long' dwells times
+  for long (orange) versus short (red) dwell time states. We define define `long' dwells times
   as the 50th percentile of all dwell times in the given state, and short as all others. It
@@
 
+  \subsection{Predominant States}\label{section:state_prevelance}
+
+  \begin{figure}[h]
+  \centering
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{prevalence_GCL.pdf}
+  \caption{ethylene glycol}\label{fig:prevalence_GCL}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{prevalence_URE.pdf}
+  \caption{urea}\label{fig:prevalence_URE}
+  \end{subfigure}
+  \begin{subfigure}{0.325\textwidth}
+  \includegraphics[width=\textwidth]{prevalence_ACH.pdf}
+  \caption{acetic acid}\label{fig:prevalence_ACH}
+  \end{subfigure}
+  \caption{MD trajectories sample the clustered states to varying degrees and
+  for varied amounts of time. For each solute in (a), (b) and (c), we plot
+  the total number of trajectories that sample a given state (blue) as well
+  as the fraction of the total simulation time spent in that state.}
+  \label{fig:state_prevalence}
+  \end{figure}
+
 \end{document}
+% LocalWords:  IHMM pdf prior's solute MSD AR HMM ACH Dirichlet delocalize hmm
+% LocalWords:  Gaussians methanol's scikit plateauing nolabel MSDs urea's URE
+% LocalWords:  shortlag evy BJC SI msds msd nclusters Solutes solutes alkane

### 2020-06-03 Ben_Manuscripts/hdphmm/Draft.tex
revised comments.
Addressed final comments

@@
   multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
-  %MRS: citation missing for coscia_chemically_2019
+
   We have already advanced our understanding of LLC monomer design in our previous work
@@
   efficiently uncover underlying transport mechanisms which give rise to different 
-  solute dynamical behavior. We cluster 
-  %MRS:
-  %similar state parameters 
-  states with similar parameters
-  across all
-  trajectories in order to reduce the total state space and to 
-  %MRS:
-  identify
-  %understand 
-  which
-  segments of the solute trajectories exhibit similar behavior. We use the 
+  solute dynamical behavior. We cluster states with similar parameters
+  across all trajectories in order to reduce the total state space and to 
+  identify which segments of the solute trajectories exhibit similar behavior. We use the 
   parameters of the clustered states identified by the HDP-AR-HMM in order to 
@@
   occupy the tail region with the rest are near the pore center.~\cite{coscia_chemically_2019}
-  %MRS: fix citation above.
 
@@
   simultaneously inferring the VAR parameters of those modes. We use the sticky model
-  in order to encourage higher self-transition probabilities since we physically expect
-  %MRS: maybe ``physically observe?'' instead of physically expect.
-  solutes to stay trapped in states for appreciable amounts of time.
+  in order to encourage higher self-transition probabilities since we physically observe
+  solute entrapment in states for appreciable amounts of time.
 
@@
   We clustered states with like parameter sets in order to reduce the state space to
-  a more easily interpretable size 
-  % CPC: perhaps keep hammering home not only reducing, but also reemphasize why absolute
-  % value of some parameters really not of interest 
-  %MRS: explain why parameters of single states don't give insight; more context needed?  Is CPC talking about
-  %MRS: some some of the parameters not being interesting in general, not just the values for some states?
-  and because the parameters of a single state alone does not always have enough context
-  to provide meaningful physical insight. For each solute studied, we identified 
-  approximately 300-500 independent states, each with separate VAR(1) parameters.
-  Many of these states exhibit very similar dynamical behavior except their mean 
-  levels in each dimension are different.
+  a more easily interpretable size and because the parameters of a single state 
+  alone does not always have enough context to provide meaningful physical insight.
+  For each solute studied, we identified approximately 300-500 independent states, 
+  each with separate VAR(1) parameters. Many of these states exhibit very similar 
+  dynamical behavior except their mean levels in each dimension are different.
 
@@
   We clustered based on the eigenvalues of $A$ and $\Sigma$, the distance from the 
-  pore center and the self-transition probabilities, $P_{ii}$, of each state. $A$ 
+  pore center and the self-transition probabilities, $T_{ii}$, of each state. $A$ 
   and $\Sigma$ quantify the temporal correlation and size of fluctuations in a 
-  given state. $P_{ii}$ is directly related to the expected time spent in each state.
+  given state. $T_{ii}$ is directly related to the expected time spent in each state.
   The distance from the closest pore center is expected to be physically meaningful
@@
 
-  To cluster on $P_{ii}$, we first cast them in terms of the expected dwell times. The expected
+  To cluster on $T_{ii}$, we first cast them in terms of the expected dwell times. The expected
   value of the number of sequential self-transitions is simply:
   \begin{equation}  
-   E[dwell~time] = \frac{1}{1 - P_{ii}}
+   E[dwell~time] = \frac{1}{1 - T_{ii}}
    \label{eqn:dwell_times}
   \end{equation}  
-  This relationship implies that dwell times approach infinity as $P_{ii}$ approaches
+  This relationship implies that dwell times approach infinity as $T_{ii}$ approaches
   1. Therefore we found the most success with agglomerative clustering by linearizing this
-  relationship and clustering on $-\log(1 - P_{ii})$.
+  relationship and clustering on $-\log(1 - T_{ii})$.
 
@@
 
-  We obtained estimates of clustered $A$ and $\Sigma$ parameters as well as a
-  %MRS: check again agreement on $T$ and $P$ - you switched to $P$, right? Or are they 2 different things?
+  We obtained estimates of clustered $A$ and $\Sigma$ parameters as well as
   consensus $T$ matrices, describing transitions between all possible clustered states 
-  %MRS: do you explicitly say how to get the consensus transition matrices?
   exhibited by the ensemble of trajectories, using the inference component of 
@@
   zeroed solute trajectories with state sequences fixed according to the remapped 
-  clustered state assignments. Simultaneous application of the HDP-AR-HMM to 
-  all trajectories as we have done is only possible because the state sequence 
-  is fixed. In cases where one does not know the state sequence and would like to 
-  incorporate data from multiple trajectories, one can apply the beta process (BP)
-  AR-HMM.~\cite{fox_sharing_2009} However the data requirements may be quite high
-  for a good parameterization, which is why we elected to follow the clustering 
-  approach described thus far.
+  clustered state assignments. This allowed us to parameterize states shared 
+  across multiple trajectories and to easily generate a single transition matrix. 
+  Simultaneous application of the HDP-AR-HMM to all trajectories as we have done 
+  is only possible because the state sequence is fixed. In cases where one does not 
+  know the state sequence and would like to infer by incorporating data from 
+  multiple trajectories, one can apply the beta process (BP) AR-HMM.~\cite{fox_sharing_2009} 
+  However the data requirements may be quite high for a good parameterization, 
+  which is why we elected to follow the clustering approach described thus far.
   %BJC: I actually found 3 different ways do this. All giving the same results.
@@
   %MRS: these should have different amounts of noise, making them hard to compare? Is this an issue?
+  %BJC: added some clarification to Method 2
   \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
-  	\item For each bootstrap trial, we generated 24 stochastic trajectories, one from
-  	each of the 24 independent HDP-AR-HMM models. The result of the trial is the mean
-  	of the MSDs calculated from each trajectory constituting the ensemble. 
-    \item We generated an ensemble of 1000 independent stochastic trajectories using
-    the clustered parameter sets. For each trial, we calculated the MSD of 1000 
-    trajectories sampled, with replacement, from the ensemble.
+  	\item For each bootstrap trial, we generated 24 stochastic trajectories since we
+  	are constrained to sample with replacement from the 24 independent HDP-AR-HMM models.
+    The result of each trial is the mean of the MSDs of the trajectories
+    constituting the bootstrapped ensemble. 
+    \item Since trajectories generated by Method 2 are based on the clustered parameter 
+    set used to define a single model, we can bootstrap on trajectory ensembles of
+    arbitrary size. For each bootstrap trial, we generated an ensemble of 1000 independent
+    stochastic trajectories, calculated the MSD of each and then sampled, with replacement,
+    from the ensemble. This larger ensemble allows us to achieve lower uncertainties with
+    the same number of bootstrap trials as Method 1. 
   \end{enumerate}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{selectivity.pdf}
-  \caption{Of the solutes studied, 
-  %MRS: add qualifier.
-  the models predict that 
-  the current generation of H\textsubscript{II}
-  LLC membranes may have the most success selectively removing acetic acid and,
-  to a lesser extent, urea from solution containing either ethylene glycol or 
-  methanol.
+  \includegraphics[width=0.6\textwidth]{selectivity2.pdf}
+  \caption{Of the solutes studied, the models predict that the current generation 
+  of H\textsubscript{II} LLC membranes may have the most success selectively removing 
+  acetic acid and, to a lesser extent, urea from solution containing either ethylene
+  glycol or methanol.
   }\label{fig:selectivity}
@@
   varies by predominant state, as seen in more detail in Figure~\ref{fig:hydrogen_bonding}.
-  %MRS: what do you think about this? It maks it easier to read.
   \begin{itemize}
-  \item States 1 and 2 primarily have hydrogen bonds to the 
-  ester groups at the ends of the monomer tails and, to a smaller extent, the ether 
-  linkages between the monomer head group and tails. 
-  \item State 1 methanol molecules that
-  donate hydrogen bonds to the tail oxygen atoms exhibit by far the longest hydrogen
-  bond lifetimes among all states. 
-  \item Methanol molecules in states 3 and 4 hydrogen 
-  bond to all regions of the monomer relatively evenly, which is consistent with our earlier observation that
+	\item States 1 and 2 primarily have hydrogen bonds to the ester groups at the ends
+	of the monomer tails and, to a smaller extent, the ether linkages between the 
+	monomer head group and tails. 
+    \item State 1 methanol molecules that donate hydrogen bonds to the tail oxygen 
+    atoms exhibit by far the longest hydrogen bond lifetimes among all states. 
+    \item Methanol molecules in states 3 and 4 hydrogen bond to all regions of the
+    monomer relatively evenly, which is consistent with our earlier observation that
     states 3 and 4 are representative of behavior seen radially throughout the membrane
@@
     is likely a high variance transitory state. 
-  \item Finally, methanol molecules in state 5
-  hydrogen bond almost exclusively to the carboxylate head groups and ether linkages 
-  which is consistent with the low (close to the pore center) radial mean of the 
-  cluster.
+    \item Finally, methanol molecules in state 5 hydrogen bond almost exclusively 
+    to the carboxylate head groups and ether linkages which is consistent with the 
+    low (close to the pore center) radial mean of the cluster.
   \end{itemize}
@@
   \centering
-  \includegraphics[width=0.6\textwidth, angle=0]{monomer_oxygens.png}
+  \includegraphics[width=0.6\textwidth, angle=0]{monomer_oxygens.pdf}
   \caption{}\label{fig:monomer_oxygens}
@@
   \end{subfigure}
+  %y-axis label being cut off?
   \caption{(a) We analyzed hydrogen bonds donated by methanol to the highlighted oxygen
@@
   \end{subfigure}
-  %BJC: Is it worth putting a bars with the solute MSDs on this plot
   \begin{subfigure}{0.49\textwidth}
@@
   to the clustered state sequences, is inversely related to the solute MSDs.
-  %MRS: this can be explained in the text.
-  %after a 1000 ns time lag.
   (d) The expected dwell time of solutes increases in states with high local 
@@
   \centering
-  \includegraphics[width=3.25in]{hdphmm_TOC.pdf}
+  \includegraphics[width=3.25in]{hdphmm_TOC_v2.pdf}
   \end{figure}

### 2020-06-03 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Addressed final comments

@@
 
-\title{Supporting Information: Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series 
-       of Solute Trajectories in Nanostructured Membranes.}
+\title{Supporting Information: Statistical Inference of Transport Mechanisms and Long Time Scale 
+	   Behavior from Time Series of Solute Trajectories in Nanostructured Membranes.}
 
@@
   equivalent to the variance of all observed fluctuations. 
-  The HDP-AR-HMM simulation appears to over-estimate the variance because the actual 
-  distribution of solute fluctuations has 
-  %MRS: heavy tails should mean larger variance? Clarify?
-  heavy tails with a smaller variance (Figure~\ref{fig:emission_widths}).
+  The HDP-AR-HMM simulation appears to over-estimate the width of the hop distribution
+  because the actual distribution of solute fluctuations has 
+  heavy tails with a smaller width (Figure~\ref{fig:emission_widths}).
   The total distribution of hops is expected to be heavy tailed because it is a

### 2020-06-10 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex
Improvements to figure readability

@@
 \usepackage{scrextend}
+\usepackage[normalem]{ulem}
 
@@
 		Author reply:
-		%BJC: modify figures
-		%BJC: cut down on interpretation in all figures
+
+		We thank the reviewer for their constructive feedback. The fontsize in the figure is indeed too small.
+		We have modified the plots in the figure to have larger, more readable font and we took this opportunity
+		to increase the font size on Figures 6--8 as well.
+
+		The reviewer is correct in their interpretation of the figures. For clarity, we modified the y axes as
+		well as the caption in order to further aid the reader. We also made efforts to cut down on the interpretation
+		that is already presented in the main text. We made similar modifications to Figure 6 since it is an
+		analogous figure. Our caption changes are presented below.
+
+		This comment caused us to reconsider the detail in the captions of other figures as well. We feel
+		the level of the detail is justified in most cases. However, we decided to remove some redundant
+		information from Figure 13, as shown below.
+
+		Figure 5, original caption:
+
+		\begin{quote}
+
+		  The parameters of the one mode model reveal differences in dynamics
+	      between solutes. (a) We parameterized Gaussian,
+	      $\mathcal{N}(\sigma)$, and L\'evy stable, $L(\sigma, \alpha_h)$,
+	      distributions to describe solute hop lengths. We assume the mean
+	      ($\mu$) to be zero for these distributions and no
+	      skewness ($\beta = 0$) in the L\'evy stable distributions. High
+	      values of $\sigma$ and lower values of $\alpha_h$ result in larger
+	      hops. (b) We parameterized a pure power law, $P(\alpha)$, and a
+	      truncated power law, $P_T(\alpha, \lambda)$, distribution to describe
+	      solute dwell times. Lower values of $\alpha$ lead to heavier power
+	      law tails and higher values of $\lambda$ truncate the distribution at
+	      lower dwell times. (c) Finally, we parameterized the hop
+	      autocorrelation function, $\gamma(H)$, to describe the degree of
+	      correlation between hops. Simulations with higher values of $H$ display
+	      behavior closer to the Brownian limit.
+
+		\end{quote}
+
+		Figure 5, modified caption:
+
+		\begin{quote}
+
+		  The parameters of the one mode model reveal differences in dynamics
+	      between solutes. (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, 
+	      and L\'evy stable, $L(\sigma, \alpha_h)$, distributions to describe
+	      solute hop lengths. 
+		  % BJC: added	      
+	      Each bar represents the value of a single parameter,
+	      highlighted in bold, of the associated hop distribution.
+		  % BJC: removed	      
+	      % We assume the mean ($\mu$) to be zero for these distributions and no
+%	      skewness ($\beta = 0$) in the L\'evy stable distributions. 
+	      In general, higher values of $\sigma$ and lower values of $\alpha_h$ 
+	      result in larger hops. 
+	      (b) We parameterized 
+	      % BJC: removed. I think this was left over from when the pure power law was still in the paper
+	      % a pure power law, $P(\alpha)$, and 
+	      a truncated power law distribution, $P_T(\alpha, \lambda)$,  to describe
+	      solute dwell times. 
+		  % BJC: not sure if should reiterate the bold highlights here.	      
+	      Lower values of $\alpha$ lead to heavier power
+	      law tails and higher values of $\lambda$ truncate the distribution at
+	      lower dwell times. (c) Finally, we parameterized the hop
+	      autocorrelation function, $\gamma(H)$, to describe the degree of
+	      correlation between hops. Simulations with higher values of $H$ display
+	      behavior closer to the Brownian limit.
+
+		\end{quote}
+
+		Figure 6, original caption:
+
+	    \begin{quote}
+
+		  The two mode model parameterizes solute behavior in the pore and tails
+	      separately. We consider solutes to be within the pore region if they
+	      are 0.75 nm from a given pore center, otherwise they are in the
+	      tails. (a) Generally, movement is much more restricted in the tail
+	      region, parameterized by lower $\sigma$ values (smaller hops) for the
+	      Gaussian and L\'evy stable distributions. Values of $\alpha_h$ are
+	      significantly lower for urea and acetic acid meaning there is a
+	      larger probability that they will take large hops. (b) Dwell times
+	      are longer in the tails. Lower values of $\alpha$ correspond to power
+	      laws with heavier tails and thus higher probabilities of long dwell
+	      times. There is no easily discernible trend in $\lambda$ of the
+	      truncated power law distribution. Note that we used the same Hurst
+	      parameter for both modes (shown in Figure~\ref{fig:hurst_barchart})
+	      due to a low number of sufficiently long sequences of hops in each
+	      mode. (c) Solutes spend various amounts of time in the tail and pore
+	      region dependent on their size, shape and chemical functionality.
+	      Methanol's small size favors occupation of the much larger accessible
+	      volume in the tails. Urea and acetic acid are fairly stable in both
+	      regions since they are small and hydrophilic. Ethylene glycol has a
+	      slight preference for the pores likely because it is a larger
+	      molecule with two hydrophilic hydroxyl groups.
+
+        \end{quote}
+
+	    Figure 6, modified caption:
+
+	    \begin{quote}
+		  % Figure 6 caption
+		  The two mode model parameterizes solute behavior in the pore and tails
+	      separately. We consider solutes to be within the pore region if they
+	      are 0.75 nm from a given pore center, otherwise they are in the
+	      tails. 
+	      %BJC: added next two sentences
+	      For (a) and (b), each bar represents the value of a single parameter, 
+	      highlighted in bold, of the associated hop or dwell time distribution.
+	      Parameterizations of solute motion in the pores are visualized as bars
+	      in the upper half of the plots, while the parameters describing motion 
+	      in the tails are reflected into the lower half of the plots.
+	      %BJC: modified this sentence to cut down on detail
+	      (a) Generally, movement is more restricted in the tail region, but 
+	      with occasionally large hops, as implied by lower $\sigma$ (smaller
+	      hops) and $\alpha_h$ (heavier tails of the hop distribution) values.
+	      %for the Gaussian and L\'evy stable distributions. 
+%	      Values of $\alpha_h$ are significantly lower for urea and acetic acid
+%	      meaning there is a larger probability that they will take large hops.
+	      (b) Dwell times are longer in the tails as implied by lower values 
+	      of $\alpha$.
+	      %correspond to power laws with heavier tails and thus higher probabilities of long dwell
+	      %times. 
+	      There is no easily discernible trend in $\lambda$ of the
+	      truncated power law distribution. Note that we used the same Hurst
+	      parameter for both modes (shown in Figure~\ref{fig:hurst_barchart})
+	      due to a low number of sufficiently long sequences of hops in each
+	      mode. (c) Solutes spend various amounts of time in the tail and pore
+	      region dependent on their size, shape and chemical functionality.
+	      %BJC: removing details that is already in the text
+%	      Methanol's small size favors occupation of the much larger accessible
+%	      volume in the tails. Urea and acetic acid are fairly stable in both
+%	      regions since they are small and hydrophilic. Ethylene glycol has a
+%	      slight preference for the pores likely because it is a larger
+%	      molecule with two hydrophilic hydroxyl groups.
+
+        \end{quote}
+
+        Figure 13, modified caption:
+
+        \begin{quote}
+
+          The selectivity between pairs of species changes monotonically with
+	      pore length. The strength of dependence on pore length depends on
+	      the difference between $\beta$ values. 
+		  %BJC: All of this is in the text.	      
+	      \sout{The largest differences in solute
+	      flux result in high selectivities at any pore length. This membrane
+	      may be a good candidate for the separation of ethylene glycol from
+	      acetic acid. Ethylene glycol has the lowest $\beta$ value while
+	      acetic acid has the second highest, leading to strong length
+	      dependence. Ethylene glycol also has the highest flux and acetic acid
+	      has the lowest resulting in relatively high selectivities independent
+	      of pore length.}
+
+        \end{quote}
 

### 2020-06-10 Ben_Manuscripts/hdphmm/cover_letter.tex
Improvements to figure readability

@@
 	Article in the ``Machine Learning in Physical Chemistry" special issue of the Journal 
-	of Physical Chemistry, specifically in section X of % BJC: the link with section titles is an unfinished webpage
-	part B of the journal. We expect this work to be of significant interest to 
-	researchers who study complex dynamics in both structured and amorphous soft 
-	materials. %BJC: this could be made more general. Maybe better focused for JPC though
+	of Physical Chemistry, specifically in part B, section B4: Fluid 
+	Interfaces, Colloids, Polymers, Soft Matter, Surfactants, and Glassy Materials.
+	We expect this work to be of significant interest to researchers who study complex 
+	dynamics in both structured and amorphous soft materials.
 
@@
 	characterizing the same set of solute center-of-mass time series trajectories
-	(Coscia and Shirts, arXiv:2004.07905 [cond-mat.soft]). % BJC: is this the right way to cite arXiv?
-	In that work, we used our qualitative understanding of solute transport 
-	(Coscia and Shirts \textit{J. Phys. Chem. B}, 123, 6314--6330 (2019)) in order
-	to formulate stochastic models which could be used to project solute behavior
+	(Coscia and Shirts, arXiv:2004.07905 [cond-mat.soft]). In that work, we used
+	our previously gained qualitative understanding of solute transport (Coscia 
+	and Shirts \textit{J. Phys. Chem. B}, 123, 6314--6330 (2019)) in order to 
+	formulate stochastic models which could be used to project solute behavior
 	on macroscopic time scales, thus allowing prediction of experimentally relevant
@@
 
-	%BJC: included phone numbers because it asked to do so in author's guide.
-	%BJC: need at least 5 reviewers
 	\noindent Some suggestions for reviewers are:
@@
 
-	    %BJC: these are reviewers suggested for the first stochastic transport paper
-	    %BJC: not sure if bad to use twice
 		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
@@
 
-		\item Coray Colina uses various simulation techniques to understand structure-property relations
-		in functional materials including nanoporous materials for separation applications. (University
-		of Florida, 352-294-3488, \href{mailto:colina@chem.ufl.edu}{colina@chem.ufl.edu}).
-
 		\item Venkat Ganesan uses multiscale modeling to study solute and ion transport in complex
@@
 		%BJC: from structure paper
-		\item Eric Jankowski has experience modeling soft materials using molecular dynamics
-		including work done simulating structure factors from simulations, much like
-		the techniques we use in our work (Boise State University, 208-426-5681,
-		\href{mailto:ericjankowski@boisestate.edu}{ericjankowski@boisestate.edu})
+		\item Eric Jankowski has experience modeling soft materials using molecular dynamics.
+		(Boise State University, 208-426-5681, \href{mailto:ericjankowski@boisestate.edu}{ericjankowski@boisestate.edu})
 
-		\item Emily Fox?  % she made the HDP-AR-HMM
+		\item Coray Colina uses various simulation techniques to understand structure-property relations
+		in functional materials including nanoporous materials for separation applications. (University
+		of Florida, 352-294-3488, \href{mailto:colina@chem.ufl.edu}{colina@chem.ufl.edu}).
 
+%		\item Martin Lindén has use variational Bayesian treatments of hidden Markov models in
+%		order to learn from thousands of single-particle trajectories.
+%		
+%		\item Steve Presse
+%		
 	\end{enumerate}

### 2020-06-12 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex
Response to more involved reviewer 2 question`

@@
   \item \textit{Micro in micrometer should be written with upright Greek letter.} \\ \\
-  		Author reply:
 
   \item \textit{d as “dt” in integrals should be non italic.} \\ \\
-  		Author reply:
 
   \item \textit{Page 10 line 28: T should be in symbol form.} \\ \\
-  		Author reply:
 
   \item \textit{Symbol T is used for both time and transition matrix, perhaps use some matrix notation.} \\ \\
-  		Author reply:
 
@@
   the most important reference for this paper is missing the volume number.} \\ \\
-		Author reply:
 \end{itemize}
+
 \end{addmargin}
+
+Author reply: We thank the reviewer for catching these errors and have corrected all of the instances
+we could identify.
 
@@
 
-    Author reply:
+    Author reply: We thank the reviewer for pushing us to increase the clarity of the abstract.
+
+    Original text:
+
+    \begin{quote}
+    Mathematically modeling complex transport phenomena can be a powerful tool
+    for extracting important physical information from molecular simulations. 
+    In this study, we present two new approaches that use stochastic time series
+    modeling to predict long time-scale behavior and macroscopic properties 
+    from molecular simulation which can be generalized to other molecular systems
+    where complex diffusion occurs. Specifically, we parameterize our models using
+    long molecular dynamics (MD) simulation trajectories of a cross-linked 
+    H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
+    predict solute mean squared displacements (MSDs), solute flux, and
+    solute selectivity in macroscopic length pores.    
+    \end{quote}
+
+	Modified text (highlighted in red):
+
+	\begin{quote}
+    Mathematically modeling complex transport phenomena can be a powerful tool
+    for extracting important physical information from molecular simulations. 
+    In this study, we present two new approaches that use stochastic time series
+    modeling to predict long time-scale behavior and macroscopic properties 
+    from molecular simulation which can be generalized to other molecular systems
+    where complex diffusion occurs. \textcolor{red}{In our previous work, we studied long 
+    molecular dynamics (MD) simulation trajectories of a cross-linked 
+    H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane where we
+    observed subdiffusive solute transport behavior characterized by intermittent
+    hops separated by periods of entrapment. In this work, we use our models to 
+    parameterize the behavior of the same systems, so we can generate characteristic
+    trajectory realizations that can be used} to predict solute mean squared 
+    displacements (MSDs), solute flux, and solute selectivity in macroscopic length pores.
+    \end{quote}
 

### 2020-06-15 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex
responses revised once over

@@
 appropriate revisions to the manuscript document. The comments have been reproduced
-in italics and all changes to the text have been documented below. In cases where 
-we modified the text we included the original text (denoted by ``Original text:") 
+in italics and all changes to the text have been documented below. 
+%BJC: Need to modify this to be more in line with what I did.
+In cases where we modified the text we included the original text (denoted by ``Original text:") 
 followed by the new text (denoted by ``New text:").
@@
   \begin{quote}
-  Each unit cell is contained $\sim$ 62,000 total atoms. % BJC: do you think he want unit cell dimensions? X x Y x Z? 
+  Each unit cell contains $\sim$ 62,000 total atoms. % BJC: do you think they want unit cell dimensions? X x Y x Z? 
   \end{quote}
@@
   water molecules using the TIP3P water model.~\cite{} We made each choice in order to
-  ensure that our approach is accessible and reproducible for a wide audience and so that
+  ensure that our approach is accessible and reproducible to a wide audience and so that
   it is easy to study a broad range of solutes and monomer chemistries in high throughput. 
@@
   diffusion. In our previous work, we have shown that monomer motion is negligible on 
-  simulation time scales. Our main focus is on the time series of the solutes in the \
-  membrane pores. On the 5 $\mu s$ time scales which we simulate we do not see any 
-  solutes cross between pores. Therefore, we expect similar solute behavior in larger
+  simulation time scales. Our main focus is on the time series of the solutes in the
+  membrane pores. On the 5 $\mu s$ time scales which we simulate, we do not observe any 
+  solutes that cross between pores. Therefore, we expect similar solute behavior in larger
   arrays of pores. A study of finite size effects may be interesting in future work, but
@@
   we fit our models to the time series.
-
-  % BJC: easy to specify force field.
-  % BJC: what to say about polarizable force fields? Focus on methods? Maybe throw in some 
-  % references to solute transport with polarizable force fields?
-  % finite size effects -- ?? sufficiently long pores in z?
-  % BJC: no gaurantee polarizable would be good since there aren't any out of the box 
-  % polarizable force fields
 
@@
 		We thank the reviewer for their constructive feedback. The fontsize in the figure is indeed too small.
-		We have modified the plots in the figure to have larger, more readable font and we took this opportunity
-		to increase the font size on Figures 6--8 as well.
+		We have modified the plots in the figure to have larger, more readable font. We also took this 
+		opportunity to increase the font size on Figures 6--8.
 
@@
 	      truncated power law distribution. Note that we used the same Hurst
-	      parameter for both modes (shown in Figure~\ref{fig:hurst_barchart})
+	      parameter for both modes (shown in Figure~\ref{M-fig:hurst_barchart})
 	      due to a low number of sufficiently long sequences of hops in each
@@
   		Author reply: We thank the reviewer for their sensible question. The simplest answer
-  		to this is that ultimately we are only concerned with transport along the pore axis. Radial
+  		to this is that ultimately, we are only concerned with transport along the pore axis. Radial
   		solute transport (with respect to the pore center) is effectively bounded and only 
-  		contributes to axial MSD to the extent that it influences axial transport. We 
+  		contributes to the axial MSD to the extent that it influences axial transport. We 
   		do acknowledge that the radial location of solutes has an influence on solute
   		hopping behavior which is why attempted to create the two mode anomalous diffusion model.
+
 		From a more mathematical standpoint, there are two factors which pose challenges with
@@
         As described in the text, the predicted MSDs of the two-mode model may indeed show better 
-        qualitative behavior than the one-mode model. Specifically, the two-mode model becomes
+        qualitative MSD behavior than the one-mode model. Specifically, the two-mode model becomes
         linear on long timescales which may be more consistent with our MD results. However, this 
@@
         framework. Applying it to the two mode model would be trivial. We chose to use the one-mode 
-        model to demonstrate because it passes our qualitative and quantitative checks and is
+        model for demonstration because it passes our qualitative and quantitative checks and is
         mathematically sound. As the reviewer points out, it is likely that our approach to 
@@
 		sample the MFPT over a 50 nm pore. This procedure becomes computationally expensive very
-		quickly, and requires ample RAM to store the trajectories as they constructed.
+		quickly, and requires ample RAM to store the trajectories as they are constructed.
 
@@
 
-		  Author reply:
-		  % BJC: maybe just give some background on this project overall. Could add a paragraph
-		  % to explain this
+		  Author reply: The reviewer makes a valid point. This work started in parallel with experimental
+		  work which promised solute flux and selectivities that we could compare directly to our
+		  simulations. However, synthesizing an aligned hexagonal phase membrane has been a practical
+		  challenge for our experimental collaborators and much of their focus has shifted to 
+		  membranes formed by liquid crystals that self-assemble into bicontinuous cubic architectures
+		  which are much simpler to synthesize. We have also started to shift our focus towards models 
+		  of the bicontinuous cubic phase. However our research into generated physically accurate 
+		  molecular models of that phase lags our work on time series modeling. In future work, we will
+		  be able to apply this technique to systems for which we have experimental data.
+
+		  %BJC: I'm not sure this is worth bringing up
+		  As far as mathematical models, there are none that we know of to which we can reasonably
+		  compare. Some work has been done to apply Donnan steric pore models to experimental data, 
+		  but these models are continuum-based and have not been used in a predictive capacity.
 
@@
 
-    %BJC: I have no problem with this
+    %BJC: I'll address this once I incorporate things into the text.
 
@@
 
+%BJC: TODO
 Author reply: We thank the reviewer for catching these errors and have corrected all of the instances

### 2020-06-16 Ben_Manuscripts/hdphmm/Draft.tex
typo.

--- 2020-06-01 Ben_Manuscripts/hdphmm/Draft.tex
@@
   %BJC: Is it worth putting a bars with the solute MSDs on this plot
+  %MRS: yeah, I think it looks good.
   \begin{subfigure}{0.49\textwidth}
@@
   This work was supported in part by the ACS Petroleum Research Fund
-  grant \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN) 
+  grant \#59814-ND7 and a Graduate Assistance in Areas of National Need (GAANN) 
   fellowship which is funded by the U.S. Department of Education. 

### 2020-06-16 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex
Comments on response to reviewers.

@@
   %BJC: use a different word?
+    %MRS: this is fine.
 
   Author reply: We thank the reviewer for identifying our potentially confusing choice of words.
-  The first sentence (Page 5 line 19) refers more broadly to the two types of stochastic models 
-  formulated in this work: the Anomalous Diffusion model and the Markov state-dependent dynamical
-  model. The second quoted sentence (Page 5 line 47) refers to the different types of
+  The first sentence (Page 5, line 19) refers more broadly to the two types of stochastic models 
+  formulated in this work: the anomalous diffusion model and the Markov state-dependent dynamical
+  %MRS: removed the capitalization on anomolous diffusion, not grammatical generally.
+  model. The second quoted sentence (Page 5, line 47) refers to the different types of
   motion (FBM and CTRW) that give rise to anomalous diffusion specifically. The paragraph expands
@@
         its reliability for this particular system (often simulations involving changed solutes
-        through pores require polarizable force fields)? Next, reading this section I would 
-        also like to know how well finite size effects are controlled for with this specific 
-        membrane and these specific solutes. Lastly, it would be natural to report the size 
-        of the system in this section (I found it eventually in the introduction after 
-        searching for it throughout the manuscript).}
+        through pores require polarizable force fields)?
+   }
 
@@
 
+  We added the following text to address comments related to our choice of force field:
+
+  New text:
+  %MRS: add what tools used to parameterize them, like tleap, also that charges are AM1-BCC.
+  %MRS: can mention that files are available in supporting information of previous paper, though
+  %MRS: less relevant to this comment.
+  \begin{quote}
+  We parameterized monomers and solutes using the Generalized Amber Force Field (GAFF)~\cite{??} and
+  water molecules using the TIP3P water model,~\cite{}
+  %MRS: tweaked
+  % We made each choice in order to
+  % ensure that our approach is accessible and reproducible to a wide audience and so that
+  %it is easy to study a broad range of solutes and monomer
+  %chemistries in high throughput.
+  GAFF is very commonly used in simulations with diverse organic chemical functionality, and was developed for consistency
+  within the AMBER ecosystem, which used TIP3P as the water mode.
+  We chose these standard force
+  fields and generalizable parameterization approaches so that a range
+  of solutes and monomers could self-consistently and easily be
+  studied.  The main goal of this work is to develop stochastic models
+  which can reproduce solute behavior on MD time scales, independent
+  of the choice of force field. In future work, it may be beneficial
+  to employ specialized force fields, including polarizable force
+  fields or other higher-order effects in order to improve
+  the accuracy of structure parameters and selectivity predictions.
+  \end{quote}
+
+  %BJC: not sure if anything should be added to text
+
+  %MRS: generally, something should be added to the text for any
+  %reviewer comment, even if just expanding what is already there to
+  %include some of the points raised by the reviewers. It shows
+  %good-faith efforts, and also if a reviewer has a concern, some
+  %readers will have it as well, so might as well head it off.
+
+  %BJC: I could use some help on justification
+\item \textit{Next, reading this section I would 
+        also like to know how well finite size effects are controlled for with this specific 
+        membrane and these specific solutes.}
+
+        %MRS: so I'm looking at
+        %https://pubs.acs.org/doi/10.1021/jp0477147 and .  I think the
+        %key point here is that most of the finite size corrections
+        %have to do with the viscosity of the bath that the solute is
+        %in.  I THINK that we can consider the viscosity essentially infinite, or at least
+        %really really high, and therefore the corrections
+
+        %MRS: also, I cut out the part about diffusing between pores,
+        %but I don't think that's what they were getting at.
+
+        %MRS: Do the solutes cross the boundary
+        %conditions in the z direction much? You say they don't cross
+        %between pores.  I don't think that's real point, though.
+
+        We have not made any explicit finite size corrections, but
+        they are less important for this work than for diffusion in
+        other soft matter systems where diffusion is studied. In our
+        previous work, we have shown that monomer diffusion is
+        negligible on simulation time scales. Finite-size corrections
+        to diffusion are primarily due to the hydrodynamics of the surroundings (cite two
+        papers I sent), and the LLC membrane (outside of
+        intramolecular motion and quasiharmonic vibration around it's
+        average position) is therefore mostly motionless, with a very
+        high effective viscosity.  This high surrounding viscosity
+        should nearly eliminate these typical finite size effects.
+        Additionally, we are usually comparing ratios of diffusion
+        when we look at selectivity, and thus finite size effects
+        should also mostly cancel out there.
+
+        Verifying that there are indeed negligible finite size effects
+        may be interesting in future work, but we do not feel it is
+        justified for this study given the computational cost of
+        studying larger systems. We also believe it would have little
+        influence on the way in which we fit our models to the time
+        series.
+
+        %Our main focus is on the time series of the solutes in the
+        %membrane pores. On the 5 $\mu s$ time scales which we
+        %simulate, we do not observe any solutes that cross between
+        %pores. Therefore, we expect similar solute behavior in larger
+        %arrays of pores.
+
+  %MRS: I think it's always good practice to have a text change
+  %corresponding to every reviewer comment, even if it's just to
+  %clarify.  This proves that MRS: we are taking the reviewer
+  %seriously.
+
+  To clarify this logic, we have added the following text:
+
+  \begin{quote}
+    Think about text here once we agree on the approach to response.
+    \end{quote}
+
+\item \textit{Lastly, it would be natural to report the size of the
+  system in this section (I found it eventually in the introduction
+  after searching for it throughout the manuscript).}
+
   We added the following text in order to inform the reader of the system's size:
@@
   \begin{quote}
+  %MRS: couldn't hurt to add cell dimensions  
   Each unit cell contains $\sim$ 62,000 total atoms. % BJC: do you think they want unit cell dimensions? X x Y x Z? 
   \end{quote}
-
-  We added the following text to address comments related to our choice of force field:
-
-  New text:
-  \begin{quote}
-  We parameterized monomers and solutes using the Generalized Amber Force Field (GAFF) and
-  water molecules using the TIP3P water model.~\cite{} We made each choice in order to
-  ensure that our approach is accessible and reproducible to a wide audience and so that
-  it is easy to study a broad range of solutes and monomer chemistries in high throughput. 
-  The main goal of this work is to develop stochastic models which can reproduce solute
-  behavior on MD time scales regardless of the force field. In future work, it may be 
-  beneficial to employ specialized force fields, like polarizable force fields in 
-  order to improve the accuracy of selectivity predictions.
-  \end{quote}
-
-  %BJC: not sure if anything should be added to text
-  %BJC: I could use some help on justification
-  With respect to finite size effects, we have not made any explicit corrections, but
-  feel they are not of great concern for this work. While the tails of the monomers from
-  different pores interact across periodic boundaries, we are not interested in their
-  diffusion. In our previous work, we have shown that monomer motion is negligible on 
-  simulation time scales. Our main focus is on the time series of the solutes in the
-  membrane pores. On the 5 $\mu s$ time scales which we simulate, we do not observe any 
-  solutes that cross between pores. Therefore, we expect similar solute behavior in larger
-  arrays of pores. A study of finite size effects may be interesting in future work, but
-  we do not feel it is justified for this study given the computational cost of studying
-  larger systems. We also believe it would have little influence on the way in which 
-  we fit our models to the time series.
 
@@
 
-		The reviewer is correct in their interpretation of the figures. For clarity, we modified the y axes as
-		well as the caption in order to further aid the reader. We also made efforts to cut down on the interpretation
-		that is already presented in the main text. We made similar modifications to Figure 6 since it is an
+		The reviewer is correct in their interpretation of the figures. For clarity, we modified the y-axes as
+		well as the caption in order to further aid the reader in reading them. We also made efforts to cut
+                down on the interpretatio that is already presented in the main text.
+                We made similar modifications to Figure 6 since it is an
 		analogous figure. Our caption changes are presented below.
@@
 
-  \item \textit{\textbf{Page 6 line 55}: The second measure of success is based on the qualitative
+  \item \textit{\textbf{Page 6, line 55}: The second measure of success is based on the qualitative
         comparison between individual realizations of solute trajectories generated ...\\ \\
@@
   		one dimension and not two (for example using cylindrical coordinates)?}
+
+    %MRS: we probably want to phrase it a bit differently.
+I'm thinking you should you lead with the fact that it is quasi-2D, since radial information is built into having different states in the pores and the tails for the MSDDM and the 2-state anomalous diffusion models, then go into the other details.
+Thoughts?
 
@@
 		from multiple dimensions. We are actively investigating a new modeling approach which 
-		allows us to overcome these issues and to use cylindrical representations with ease.
+		allows us to overcome these issues and to use cylindrical representations with ease. %MRS: could cite the arXiv paperhere.
 
@@
         linear on long timescales which may be more consistent with our MD results. However, this 
-        long time scale linear behavior of the two-mode model has only a mathematical basis and
-        no physical basis. As discussed in the text, the one-mode model has persistent curvature
+        long time scale linear behavior of the two-mode model has
+        %MRS: one  could argue that the fact the behavior is wrong means there's no mathematical basis - or the wrong mathematical basis, so simplifying.
+        %only a mathematical basis and
+        no physical basis.
+        As discussed in the text, the one-mode model has persistent curvature
         since hop correlation persists indefinitely for fractional motion. However, for the two-mode
@@
 
+        To clarify this, we have modified the text
+        \begin{quote}
+          Text here:
+          %MRS: Ben, choose where to put this.  It could be a simple one sentence modification or addition - you probably do explain why no 2-mode model, don't you?
+        \end{quote}
   \item \textit{\textbf{Page 35 line 20-42:}\\
@@
 	  	%BJC: Could reasonably go beyond 50 nm but 7 microns becomes tough
+                %MRS: probably should explain that you COULD have gone beyond 50 nm, but there was no need, since it didn't improve the fit (if that is true).
+
 	  	%BJC: building in the correlation structure is computationally expensive. Reference a paper describing how FBM is simulated
@@
 	  	%BJC: truncated correlation functions may allow us to surpass the limitation
+
+                %MRS: could also point out that we have come up with a
+                %better approach along similar lines now (could cite arXiv paper), and so
+                %continuing down this route is probably unnneeded.
 
@@
 		  which are much simpler to synthesize. We have also started to shift our focus towards models 
-		  of the bicontinuous cubic phase. However our research into generated physically accurate 
+		  of the bicontinuous cubic phase, which do have much more experiemntal data. However, our research
+                  into generating physically accurate 
 		  molecular models of that phase lags our work on time series modeling. In future work, we will
-		  be able to apply this technique to systems for which we have experimental data.
+		  be able to apply this technique to these bicontinuous systems for which we have experimental data.
 
 		  %BJC: I'm not sure this is worth bringing up
+
+                  %MRS: probably should bring them up, since it allows you
+                  %to respond to the question, and point out they are
+                  %really insufficient because of he level of chemical
+                  %detail.  Can just put them in the introduction
+                  %describing the sort of model we want to move beyond.
+
 		  As far as mathematical models, there are none that we know of to which we can reasonably
@@
     %BJC: I'll address this once I incorporate things into the text.
+    %MRS: yeah, we don't want people to have to read thoroughly twice.
 
@@
 	\begin{quote}
-    Mathematically modeling complex transport phenomena can be a powerful tool
-    for extracting important physical information from molecular simulations. 
+    %MRS: some suggested tweaks to describe the process more directly.
+    \textcolor{red}{Using molecular simulations to fit mathematical models of complex transport phenomena
+    that have more direct connection to experimental observables
+    can be a powerful tool
+    for extracting important physical information from these molecular simulations}. 
     In this study, we present two new approaches that use stochastic time series

### 2020-06-18 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex
Brief revision of responses

@@
 
-  %BJC: use a different word?
-    %MRS: this is fine.
-
   Author reply: We thank the reviewer for identifying our potentially confusing choice of words.
@@
   formulated in this work: the anomalous diffusion model and the Markov state-dependent dynamical
-  %MRS: removed the capitalization on anomolous diffusion, not grammatical generally.
   model. The second quoted sentence (Page 5, line 47) refers to the different types of
@@
   In this first approach, we treat our system in terms of two well-known types of molecular
-  motion that leads to anomalous subdiffusion: 
+  motion which lead to anomalous subdiffusion: 
   \end{quote}
@@
   New text:
-  %MRS: add what tools used to parameterize them, like tleap, also that charges are AM1-BCC.
-  %MRS: can mention that files are available in supporting information of previous paper, though
-  %MRS: less relevant to this comment.
   \begin{quote}
-  We parameterized monomers and solutes using the Generalized Amber Force Field (GAFF)~\cite{??} and
-  water molecules using the TIP3P water model,~\cite{}
-  %MRS: tweaked
-  % We made each choice in order to
-  % ensure that our approach is accessible and reproducible to a wide audience and so that
-  %it is easy to study a broad range of solutes and monomer
-  %chemistries in high throughput.
-  GAFF is very commonly used in simulations with diverse organic chemical functionality, and was developed for consistency
-  within the AMBER ecosystem, which used TIP3P as the water mode.
-  We chose these standard force
-  fields and generalizable parameterization approaches so that a range
-  of solutes and monomers could self-consistently and easily be
-  studied.  The main goal of this work is to develop stochastic models
-  which can reproduce solute behavior on MD time scales, independent
-  of the choice of force field. In future work, it may be beneficial
-  to employ specialized force fields, including polarizable force
-  fields or other higher-order effects in order to improve
-  the accuracy of structure parameters and selectivity predictions.
+  We modeled water molecules using the TIP3P water model,~\cite{} We used the
+  antechamber module shipped with AmberTools18 to parameterize monomers and solutes
+  using the Generalized Amber Force Field (GAFF).~\cite{??} We assigned charges using
+  the AM1-BCC model. GAFF is very commonly used in simulations with diverse organic
+  chemical functionality, and was developed for consistency within the AMBER ecosystem,
+  which used TIP3P as the water model. We chose these standard force fields and
+  generalizable parameterization approaches so that a range of solutes and monomers 
+  could self-consistently and easily be studied.  The main goal of this work is to 
+  develop stochastic models which can reproduce solute behavior on MD time scales, 
+  independent of the choice of force field. In future work, it may be beneficial
+  to employ specialized force fields, including polarizable force fields or other 
+  higher-order effects in order to improve the accuracy of structure parameters and
+  selectivity predictions.
   \end{quote}
 
-  %BJC: not sure if anything should be added to text
-
-  %MRS: generally, something should be added to the text for any
-  %reviewer comment, even if just expanding what is already there to
-  %include some of the points raised by the reviewers. It shows
-  %good-faith efforts, and also if a reviewer has a concern, some
-  %readers will have it as well, so might as well head it off.
-
-  %BJC: I could use some help on justification
-\item \textit{Next, reading this section I would 
-        also like to know how well finite size effects are controlled for with this specific 
-        membrane and these specific solutes.}
+\item \textit{Next, reading this section I would also like to know how well finite 
+			  size effects are controlled for with this specific membrane and these 
+			  specific solutes.}
 
@@
 
-        %MRS: also, I cut out the part about diffusing between pores,
-        %but I don't think that's what they were getting at.
-
-        %MRS: Do the solutes cross the boundary
-        %conditions in the z direction much? You say they don't cross
-        %between pores.  I don't think that's real point, though.
-
-        We have not made any explicit finite size corrections, but
-        they are less important for this work than for diffusion in
-        other soft matter systems where diffusion is studied. In our
-        previous work, we have shown that monomer diffusion is
-        negligible on simulation time scales. Finite-size corrections
-        to diffusion are primarily due to the hydrodynamics of the surroundings (cite two
-        papers I sent), and the LLC membrane (outside of
-        intramolecular motion and quasiharmonic vibration around it's
-        average position) is therefore mostly motionless, with a very
-        high effective viscosity.  This high surrounding viscosity
-        should nearly eliminate these typical finite size effects.
-        Additionally, we are usually comparing ratios of diffusion
-        when we look at selectivity, and thus finite size effects
+        We have not made any explicit finite size corrections, but they are less 
+        important for this work than for diffusion in other soft matter systems 
+        where diffusion is studied. In our previous work, we have shown that 
+        monomer diffusion is negligible on simulation time scales. Finite-size 
+        corrections to diffusion are primarily due to the hydrodynamics of the 
+        surroundings (cite two papers I sent), and the LLC membrane (outside of
+        intramolecular motion and quasiharmonic vibration around it's average 
+        position) is therefore mostly motionless, with a very high effective 
+        viscosity. This high surrounding viscosity should nearly eliminate these
+        typical finite size effects. Additionally, we are usually comparing ratios
+        of diffusion when we look at selectivity, and thus finite size effects
         should also mostly cancel out there.
 
-        Verifying that there are indeed negligible finite size effects
-        may be interesting in future work, but we do not feel it is
-        justified for this study given the computational cost of
-        studying larger systems. We also believe it would have little
-        influence on the way in which we fit our models to the time
-        series.
-
-        %Our main focus is on the time series of the solutes in the
-        %membrane pores. On the 5 $\mu s$ time scales which we
-        %simulate, we do not observe any solutes that cross between
-        %pores. Therefore, we expect similar solute behavior in larger
-        %arrays of pores.
+        Verifying that there are indeed negligible finite size effects may be 
+        interesting in future work, but we do not feel it is justified for this 
+        study given the computational cost of studying larger systems. We also 
+        believe it would have little influence on the way in which we fit our models
+        to the time series.
 
@@
 
-\item \textit{Lastly, it would be natural to report the size of the
-  system in this section (I found it eventually in the introduction
-  after searching for it throughout the manuscript).}
+\item \textit{Lastly, it would be natural to report the size of the system in this
+              section (I found it eventually in the introduction after searching for it 
+              throughout the manuscript).}
 
@@
 		well as the caption in order to further aid the reader in reading them. We also made efforts to cut
-                down on the interpretatio that is already presented in the main text.
-                We made similar modifications to Figure 6 since it is an
-		analogous figure. Our caption changes are presented below.
+        down on the interpretation that is already presented in the main text. We made similar modifications
+        to Figure 6 since it is an analogous figure. Our caption changes are presented below.
 
@@
 Thoughts?
+    %BJC: modified to lead with quasi-2D
 
-  		Author reply: We thank the reviewer for their sensible question. The simplest answer
-  		to this is that ultimately, we are only concerned with transport along the pore axis. Radial
-  		solute transport (with respect to the pore center) is effectively bounded and only 
-  		contributes to the axial MSD to the extent that it influences axial transport. We 
-  		do acknowledge that the radial location of solutes has an influence on solute
-  		hopping behavior which is why attempted to create the two mode anomalous diffusion model.
+  		Author reply: We thank the reviewer for their sensible question. First, we would like
+  		to point out that the two mode anomalous diffusion model was a quasi-2D 
+  		modeling approach. In the paper, we do acknowledge that the radial location of solutes has
+  		an influence on solute hopping behavior. However, we are primarily interested in axial 
+  		transport, therefore the radial behavior is only important to the extent that it
+  		affects solute motion in that direction.
 
@@
         linear on long timescales which may be more consistent with our MD results. However, this 
-        long time scale linear behavior of the two-mode model has
-        %MRS: one  could argue that the fact the behavior is wrong means there's no mathematical basis - or the wrong mathematical basis, so simplifying.
-        %only a mathematical basis and
-        no physical basis.
-        As discussed in the text, the one-mode model has persistent curvature
-        since hop correlation persists indefinitely for fractional motion. However, for the two-mode
-        model, each time a solute transitions between the pore and tail regions, we must generate a
-        new FBM process because we lack a proven technique for simulating fractional 
-        motion that incorporates time-dependent variation in the width of the hop length 
-        distributions.
+        long time scale linear behavior of the two-mode model has no physical basis. As discussed
+        in the text, the one-mode model has persistent curvature since hop correlation persists 
+        indefinitely for fractional motion. However, for the two-mode model, each time a solute 
+        transitions between the pore and tail regions, we must generate a new FBM process because
+        we lack a proven technique for simulating fractional motion that incorporates time-dependent
+        variation in the width of the hop length distributions.
 

### 2020-07-12 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex
Incorporated reviewer responses into main document

@@
 We thank the reviewers for carefully reading over our manuscript and providing
-helpful comments. We have taken the suggestions into consideration and made
-appropriate revisions to the manuscript document. The comments have been reproduced
-in italics and all changes to the text have been documented below. 
-%BJC: Need to modify this to be more in line with what I did.
-In cases where we modified the text we included the original text (denoted by ``Original text:") 
-followed by the new text (denoted by ``New text:").
+thoughtful and constructive feedback. We have taken the suggestions into consideration 
+and made appropriate revisions to the manuscript document. The comments have been reproduced
+in italics and all changes to the text have been documented below them. Any newly added
+references are given in the bibliography of this document and are placed in the main 
+text with appropriate numbering.
 
@@
 
+  % comment 1
   \item \textit{\textbf{Page 5 line 19:} In this work, we use the output of our MD simulations
@@
 
+  % comment 2  
   \item \textit{\textbf{MD-section} \\
@@
   \begin{quote}
-  We modeled water molecules using the TIP3P water model,~\cite{} We used the
-  antechamber module shipped with AmberTools18 to parameterize monomers and solutes
-  using the Generalized Amber Force Field (GAFF).~\cite{??} We assigned charges using
-  the AM1-BCC model. GAFF is very commonly used in simulations with diverse organic
-  chemical functionality, and was developed for consistency within the AMBER ecosystem,
-  which used TIP3P as the water model. We chose these standard force fields and
-  generalizable parameterization approaches so that a range of solutes and monomers 
-  could self-consistently and easily be studied.  The main goal of this work is to 
-  develop stochastic models which can reproduce solute behavior on MD time scales, 
-  independent of the choice of force field. In future work, it may be beneficial
-  to employ specialized force fields, including polarizable force fields or other 
-  higher-order effects in order to improve the accuracy of structure parameters and
-  selectivity predictions.
+  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
+  We used the antechamber module shipped with AmberTools18 to parameterize monomers and 
+  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
+  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
+  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
+  and was developed for consistency within the AMBER ecosystem, which used TIP3P as the
+  water model. We chose these standard force fields and generalizable parameterization 
+  approaches so that a range of solutes and monomers could be self-consistently and easily 
+  studied. The main goal of this work is to develop stochastic models which can reproduce
+  solute behavior on MD time scales, independent of the choice of force field. In future 
+  work, it may be beneficial to employ specialized force fields, including polarizable 
+  force fields or other higher-order effects in order to improve the accuracy of structure 
+  parameters and selectivity predictions.
   \end{quote}
 
+  % comment 3
   \item \textit{Next, reading this section I would also like to know how well finite 
@@
 			  specific solutes.}
+
+		Author reply:
 
@@
         corrections to diffusion are primarily due to the hydrodynamics of the 
-        surroundings (cite two papers I sent), and the LLC membrane (outside of
-        intramolecular motion and quasiharmonic vibration around it's average 
-        position) is therefore mostly motionless, with a very high effective 
-        viscosity. This high surrounding viscosity should nearly eliminate these
-        typical finite size effects. Additionally, we are usually comparing ratios
-        of diffusion when we look at selectivity, and thus finite size effects
-        should also mostly cancel out there.
+        surroundings~\cite{venable_lipid_2017,yeh_system-size_2004}, and the LLC
+        membrane (outside of intramolecular motion and quasiharmonic vibration 
+        around its average position) is therefore mostly motionless, with a very
+        high effective viscosity. This high surrounding viscosity should nearly 
+        eliminate these typical finite size effects. Additionally, we are usually 
+        comparing ratios of diffusion when we look at selectivity, and thus finite 
+        size effects should also mostly cancel out there.
 
@@
 
-  To clarify this logic, we have added the following text:
-
+  %BJC: MRS, can you check my placement of this paragraph in main text (search "r1_comment3" in Final_Draft_JCTC.tex)
+  To clarify this logic, we have added the following text and citations:
   \begin{quote}
-    Think about text here once we agree on the approach to response.
+    Although we studied diffusion, we did not explicitly account for finite size effects
+    in this system. Finite size corrections to diffusion are primarily due to the
+    hydrodynamics of the surroundings~\cite{venable_lipid_2017,yeh_system-size_2004}, and
+    as discussed in our previous work~\cite{coscia_understanding_2019} the LLC membrane
+    (outside of intramolecular motion and quasiharmonic vibration around it's average 
+    position) is mostly motionless, and therefore has a very high effective viscosity.
+    Nonetheless, studies of finite size effects in this system may be worthwhile in
+    future work. However, it likely would not affect the modeling approach described in
+    this work.
   \end{quote}
 
+  % comment 4      
   \item \textit{Lastly, it would be natural to report the size of the system in this
@@
 
-  We added the following text in order to inform the reader of the system's size:
+              Author reply:
 
-  New text:
+              We thank the reviewer for pointing out this missing piece of information. We
+              have added the following text in order to inform the reader of the system's size:
 			  \begin{quote} 
-  %MRS: couldn't hurt to add cell dimensions  
-  Each unit cell contains $\sim$ 62,000 total atoms. % BJC: do you think they want unit cell dimensions? X x Y x Z? 
+			  Each unit cell contains $\sim$ 62,000 total atoms.
 			  \end{quote}
 
+  %comment 5
   \item \textit{\textbf{Figure 5 page 25:} \\
@@
 
+  % comment 6
   \item \textit{\textbf{Page 6, line 55}: The second measure of success is based on the qualitative
@@
 		similarity beyond the checks which we show in this work. Autocorrelation is indeed an input 
-		to the anomalous diffusion and Markov state-dependent dynamical model, specifically through
+		to the anomalous diffusion and Markov state-dependent dynamical models, specifically through
 		the Hurst parameter which is generated by fitting to autocorrelation of solute jumps. The
@@
 
+		%BJC: I don't think we need to modify the text for this comment?
+
+  % comment 7
   \item \textit{One question that came to mind reading the paper was: why is the model only in 
@@
   		Author reply: We thank the reviewer for their sensible question. First, we would like
-  		to point out that the two mode anomalous diffusion model was a quasi-2D 
+  		to point out that the two mode anomalous diffusion model is a quasi-2D 
   		modeling approach. In the paper, we do acknowledge that the radial location of solutes has
@@
 		from multiple dimensions. We are actively investigating a new modeling approach which 
-		allows us to overcome these issues and to use cylindrical representations with ease. %MRS: could cite the arXiv paperhere.
+		allows us to overcome these issues and to use cylindrical representations with ease. 
+		%MRS: could cite the arXiv paper here.
+		%BJC: currently not on arXiv
 
+  % comment 8
   \item \textit{\textbf{Page 35 line 12-14}: \\
@@
 
-        To clarify this, we have modified the text
+        Original text:
         \begin{quote}
-          Text here:
-          %MRS: Ben, choose where to put this.  It could be a simple one sentence modification or addition - you probably do explain why no 2-mode model, don't you?
+        We do not consider the two mode AD model because it has a broken correlation structure 
+        and we do not consider the MSDDM because its realizations do not display the expected 
+        hopping and trapping behavior. 
         \end{quote}
+
+        New text:
+        \begin{quote}
+        Although it would be trivial to test the two mode model as well, we chose not to because
+        we feel the results would be misleading to the reader since the stochastic trajectories
+        generated by this method lack a firm physical basis as discussed in Section~\ref{M-section:AD_all_data}. 
+        We also do not consider the MSDDM because its realizations do not display the expected 
+        hopping and trapping behavior. 
+        \end{quote}
+
+  % comment 9
   \item \textit{\textbf{Page 35 line 20-42:}\\
@@
 
-	  	%BJC: Could reasonably go beyond 50 nm but 7 microns becomes tough
-                %MRS: probably should explain that you COULD have gone beyond 50 nm, but there was no need, since it didn't improve the fit (if that is true).
+        We have modified the text to express the current limitations in a more straightforward manner:
 
-	  	%BJC: building in the correlation structure is computationally expensive. Reference a paper describing how FBM is simulated
-	  	%BJC: could benefit from optimized libraries, but python isn't fast enough
-	  	%BJC: also need to specify the number of steps to take beforehand
-	  	%BJC: truncated correlation functions may allow us to surpass the limitation
+	  	Original text:
+	  	\begin{quote}
+	  	The RAM requirements and performance scales greater than linearly and thus would take an 
+	  	infeasible amount of memory and time to simulate transport through a pore over 100 times
+        longer. 
+	  	\end{quote}
 
-                %MRS: could also point out that we have come up with a
-                %better approach along similar lines now (could cite arXiv paper), and so
-                %continuing down this route is probably unnneeded.
+	  	Modified text:
+	  	\begin{quote}
+	  	At this time, it is infeasible for us to simulate transport through a pore over 100 times
+	  	longer without investing significant effort into writing and optimizing new code that can
+	  	handle simulation of large trajectories with correlation between all steps.
+	  	\end{quote}
 
+  % comment 10        
   \item \textit{In this paper the models are only evaluated by their ability of achieving 
@@
 		  which are much simpler to synthesize. We have also started to shift our focus towards models 
-		  of the bicontinuous cubic phase, which do have much more experiemntal data. However, our research
-                  into generating physically accurate 
-		  molecular models of that phase lags our work on time series modeling. In future work, we will
-		  be able to apply this technique to these bicontinuous systems for which we have experimental data.
+		  of the bicontinuous cubic phase, which do have much more experimental data. However, our 
+		  research into generating physically accurate molecular models of that phase lags our work on
+		  time series modeling. In future work, we will be able to apply this technique to these 
+		  bicontinuous systems for which we have experimental data.
 
@@
 
+		  We have added a mention of these mathematical models to the introduction in order to give
+		  a more complete picture of the modeling approaches which preceded molecular dynamics:
+		  \begin{quote}
+		    Some work has been done to apply Donnan steric pore models to experimental LLC membrane 
+		    data, but these models are continuum-based and are not effective as tools for explaining
+		    complex solute-membrane interactions.~\cite{hatakeyama_water_2011}
+		  \end{quote}
+
   \end{enumerate}
@@
 
-    %BJC: I'll address this once I incorporate things into the text.
-    %MRS: yeah, we don't want people to have to read thoroughly twice.
+	We thank the reviewer for their constructive feedback. In response we have reduced our usage of
+	acronyms for the various stochastic models in favor of their full unabbreviated form for clarity.
 
@@
   \item \textit{Symbol T is used for both time and transition matrix, perhaps use some matrix notation.} \\ \\
+  %BJC: Maybe change matrix to bold italic? https://tex.stackexchange.com/questions/199789/which-bold-style-is-recommended-for-matrix-notation
 
@@
 
-%BJC: TODO
 Author reply: We thank the reviewer for catching these errors and have corrected all of the instances
@@
 
+    % comment 1
     \item \textit{ Abstract: here it is difficult to understand what is meant with "dwell times, hop 
@@
 
-    Author reply: We thank the reviewer for pushing us to increase the clarity of the abstract.
+    Author reply: We thank the reviewer for pushing us to increase the clarity of the abstract. We have
+    made the following changes in order to give more immediate context to our work.
 
@@
 
+    % comment 2
     \item \textit{Some of the acronyms were not defined (or perhaps I missed them), for example 'AD' 
@@
 
+    We thank the reviewer for pointing out these oversights. We have also defined MLE as maximum
+    likelihood estimate before its first usage. In consideration of this comment and a similar
+    comment by reviewer 1, we have decided to reduce the number of abbreviations in the main text 
+    in order to eliminate confusion over acronyms.
+
+    % comment 3
     \item \textit{In the Introduction, specifically the last paragraph of page 3 and first paragraph
@@
 
+    We thank the reviewer for this suggested improvement and we have added the appropriate
+    figure reference with some modifications to maintain the overall sentence flow:
+
+    Original text:
+    \begin{quote}  
+    We identified three mechanisms responsible for the solute trapping behavior: 
+    \end{quote}
+
+    Modified text:
+    \begin{quote}
+    The complex membrane topology (see~\ref{M-fig:membrane_structure}) gives rise to
+    three mechanisms responsible for the solute trapping behavior: 
+    \end{quote}
+
     \item \textit{Caption of Figure 7 should refer the reader to Table 2 for completeness}
@@
 
+    We thank the reviewer for helping increase the clarity of the manuscript. We have added
+    the following text to the caption of Figure 7:
+    \begin{quote}
+    The state numbers correspond to those described in Table 2.
+	\end{quote}
+
 \end{enumerate}
 
-%\bibliographystyle{ieeetr}
-%\bibliography{transport}
+\bibliographystyle{ieeetr}
+\bibliography{stochastic_transport}
 

### 2020-07-12 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
added TOC graphic
Improvements to figure readability
Incorporated reviewer responses into main document

@@
 \usepackage{array}
+\usepackage{upgreek}
 
@@
 
-  Mathematically modeling complex transport phenomena can be a powerful tool
-  for extracting important physical information from molecular simulations. 
-  In this study, we present two new approaches that use stochastic time series
-  modeling to predict long time-scale behavior and macroscopic properties 
-  from molecular simulation which can be generalized to other molecular systems
-  where complex diffusion occurs. Specifically, we parameterize our models using
-  long molecular dynamics (MD) simulation trajectories of a cross-linked 
-  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
-  predict solute mean squared displacements (MSDs), solute flux, and
-  solute selectivity in macroscopic length pores.
+  % BJCR: r2_comment2 - replacement to following commented out paragraph  
+  Using molecular simulations to fit mathematical models of complex transport phenomena
+  that have more direct connection to experimental observables can be a powerful tool
+  for extracting important physical information from these molecular simulations. 
+  In this study, we present two new approaches that use stochastic time series modeling
+  to predict long timescale behavior and macroscopic properties from molecular 
+  simulation which can be generalized to other molecular systems where complex 
+  diffusion occurs. In our previous work, we studied long molecular dynamics (MD) 
+  simulation trajectories of a cross-linked H\textsubscript{II} phase lyotropic liquid
+  crystal (LLC) membrane where we observed subdiffusive solute transport behavior 
+  characterized by intermittent hops separated by periods of entrapment. In this work,
+  we use our models to parameterize the behavior of the same systems, so we can generate
+  characteristic trajectory realizations that can be used to predict solute mean squared 
+  displacements, solute flux, and solute selectivity in macroscopic length pores.
+
+%  Mathematically modeling complex transport phenomena can be a powerful tool
+%  for extracting important physical information from molecular simulations. 
+%  In this study, we present two new approaches that use stochastic time series
+%  modeling to predict long timescale behavior and macroscopic properties 
+%  from molecular simulation which can be generalized to other molecular systems
+%  where complex diffusion occurs. Specifically, we parameterize our models using
+%  long molecular dynamics (MD) simulation trajectories of a cross-linked 
+%  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
+%  predict solute mean squared displacements (MSDs), solute flux, and
+%  solute selectivity in macroscopic length pores.
 
@@
   work therefore helps to connect microscopic, chemically-dependent solute 
-  motions that do not follow simple diffusive behavior with long time-scale 
+  motions that do not follow simple diffusive behavior with long timescale 
   behavior, in an approach generalizable to many types of molecular systems 
@@
 
-  There is a large disparity between the time scales accessible to atomistic 
+  There is a large disparity between the timescales accessible to atomistic 
   molecular dynamics (MD) simulations and experiment. The dynamics of molecules 
   over nanoseconds of simulation may tell a very different story than that 
-  inferred by bulk measurements on the time-scale of seconds. Understanding 
-  complex dynamical behavior on short time-scales and connecting them with much
-  longer time-scales can provide fundamental insight which can be used for 
+  inferred by bulk measurements on the timescale of seconds. Understanding 
+  complex dynamical behavior on short timescales and connecting them with much
+  longer timescales can provide fundamental insight which can be used for 
   atomic level design of materials. In this work, we pursue this connection 
@@
   could not be explained beyond speculation and vague empirical
-  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
-  can provide the resolution necessary to identify molecular interactions that
-  are key to separation mechanisms, allowing us to move beyond Edisonian design
-  approaches.
+  correlations.~\cite{dischinger_application_2017} 
+  % r1_comment10 -new text  
+  Some work has been done to apply
+  Donnan steric pore models to experimental LLC membrane data, but these models 
+  are continuum-based and are not effective as tools for explaining complex
+  solute-membrane interactions.~\cite{hatakeyama_water_2011} 
+  Atomistic molecular modeling can provide the 
+  resolution necessary to identify molecular interactions that are key to separation
+  mechanisms, allowing us to move beyond more traditional Edisonian design approaches.
 
@@
   we observed subdiffusive transport behavior characterized by intermittent
-  hops separated by periods of entrapment. We identified three mechanisms
+  hops separated by periods of entrapment. 
+  % We identified 
+  % BJCR: r2_comment3 - modified to work in figure reference
+  The complex membrane topology (see Figure~\ref{fig:membrane_structure}) gives rise
+  to
+  three mechanisms
   responsible for the solute trapping behavior: entanglement among monomer
@@
   least 62,000 atoms) it is prohibitively expensive and time-consuming to run
-  simulations longer than those performed for this work ($\sim$5 $\mu$s). Even
+  simulations longer than those performed for this work ($\sim$5 $\upmu$s). Even
   with the relatively large size of our system, we only simulate 24 solute
@@
   their inputs are parameterized using a substantial amount of data generated
-  by long ($\geq 5~\mu$s) MD simulations. Where sufficiently close to observed data,
+  by long ($\geq 5~\upmu$s) MD simulations. Where sufficiently close to observed data,
   these fitted models provide a way to propagate information about solute 
-  trajectories gathered at the microsecond time scale to realistic experimental 
-  time scales.
+  trajectories gathered at the microsecond timescale to realistic experimental 
+  timescales.
 
@@
   of a much more diverse set of behavior, including subdiffusion, a type of 
-  anomalous diffusion exhibited by solutes on the simulation time scales of this
+  anomalous diffusion exhibited by solutes on the simulation timescales of this
   study.~\cite{klages_anomalous_2008}
 
-  We treat our system in terms of two well-known classes of anomalous
-  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
-  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
-  FBM is common in crowded, viscoelastic environments where each jump comes 
-  from a Gaussian distribution but is anti-correlated to its previous steps.
-  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
-  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
-  where trajectories consist of sequential independent random draws from each
-  distribution.~\cite{montroll_random_1965} If the draws are not independent,
-  then the hop sequence generation process can be described as subordinate to
-  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
-  suggesting an FBM process is subordinate to the CTRW.
+%  We treat our system in terms of two well-known classes of anomalous
+%  subdiffusion: 
+  \label{r1_comment1}  % BJCR: replaced first sentence
+  In this first approach, we treat our system in terms of two well-known types
+  of molecular motion which lead to anomalous subdiffusion:   
+  fractional Brownian motion (FBM) subordinate to a 
+  continuous time random walk (CTRW), or subordinated fractional Brownian motion
+  (sFBM) for short. Fractional Brownian motion is common in crowded, viscoelastic 
+  environments where each jump comes from a Gaussian distribution but is 
+  anti-correlated to its previous steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
+  A pure continuous time random walk is characterized by a distribution of hop 
+  lengths and dwell times, where trajectories consist of sequential independent
+  random draws from each distribution.~\cite{montroll_random_1965} If the draws
+  are not independent, then the hop sequence generation process can be described 
+  as subordinate to the continuous time random walk. In our case, we observe 
+  anti-correlated draws from the hop distribution suggesting a subordinated 
+  fractional motion process. % is subordinate to the continuous time random walk.
 
@@
   behavior, one may gain additional insight by formulating a state-based model,
-  such as Markov state models (MSMs). MSMs are a popular class of models used
-  to project long timescale system properties based on molecular simulation
+  such as a Markov state model. Markov state models are a popular class of models
+  used to project long timescale system properties based on molecular simulation
   trajectories by identifying different dynamical modes and quantifying the
-  rates of transitions between them. MSMs are frequently used to study systems
-  with slow dynamics, such as protein
+  rates of transitions between them. Markov state models are frequently used to
+  study systems with slow dynamics, such as protein 
   folding.~\cite{snow_how_2005,chodera_automatic_2007} Researchers typically
@@
 
-  Our second modeling approach applies an extended MSM framework to a
-  relatively small set of known states based on the three previously observed
-  solute trapping mechanisms. Standard MSMs are typically applied to determine
-  equilibrium populations of states and the kinetics of transitions between
-  those states.~\cite{bowman_using_2009} We extend the framework to include
-  state-dependent fluctuations and correlations in solute position. The model
-  determines the magnitude of a solute's fluctuations from its average trapped
-  position and the degree of correlation with previous fluctuations by its current
-  state. To distinguish our approach from standard MSMs, we have named it the
+  Our second modeling approach applies an extended Markov state modeling 
+  framework to a relatively small set of known states based on the three 
+  previously observed solute trapping mechanisms. Standard Markov state models
+  are typically applied to determine equilibrium populations of states and 
+  the kinetics of transitions between those states.~\cite{bowman_using_2009}
+  We extend the framework to include state-dependent fluctuations and 
+  correlations in solute position. The model determines the magnitude of a 
+  solute's fluctuations from its average trapped position and the degree of 
+  correlation with previous fluctuations by its current state. To distinguish 
+  our approach from standard Markov state models, we have named it the
   Markov state-dependent dynamical model (MSDDM).
@@
   We determine the degree of success of our modeling approaches in two ways.
-  First, if we can closely reproduce solute MSDs measured from MD simulations
-  with realizations of our models, then it is likely that the model
+  First, if we can closely reproduce solute mean squared displacements
+  measured from MD simulations with realizations of our models, then it is likely that the model
   sufficiently captures solute dynamics and can be used in a predictive
@@
   they both have potential value dependent on a given research study's goals.
-  The AD approach provides a systematic way to compare the dynamical behavior
-  of different solutes based solely on the time series of their center of mass
-  positions. The process of choosing the correct AD approach provides its own
-  mechanistic insight since it requires a thorough analysis of solute time
-  series behavior. One can simulate different solutes, compare the fit model
-  parameters and relate them back to differences in solute size and chemical
-  composition. The MSDDM characterizes explicitly defined trapping mechanisms,
+  The anomalous diffusion approach provides a systematic way to compare the
+  dynamical behavior of different solutes based solely on the time series of 
+  their center of mass positions. The process of choosing the correct anomlous
+  diffusion modeling approach provides its own mechanistic insight since it 
+  requires a thorough analysis of solute time series behavior. One can simulate
+  different solutes, compare the fit model parameters and relate them back to 
+  differences in solute size and chemical composition. The Markov state-dependent
+  dynamical model characterizes explicitly defined trapping mechanisms,
   providing a clear picture of solute behavior while in each trapped state as
   well as the equilibrium occupation of each trapping state.  It is possible to
-  use the two modeling approaches in tandem, the AD approach to identify
-  mechanisms, and the MSDDM to characterize mechanisms.
+  use the two modeling approaches in tandem, the anomalous diffusion approach to
+  identify mechanisms, and the Markov state-dependent dynamical model to 
+  characterize mechanisms.
 
@@
 
-  Finally, we demonstrate how one can use stochastically generated realizations
-  of our models in order to predict solute flux and selectivity in pores of 
+  Finally, we demonstrate how one can use stochastically generated trajectory 
+  realizations in order to predict solute flux and selectivity in pores of 
   macroscopic length, thus achieving a better understanding of macroscopic 
@@
   atomistic molecular model of four pores in a monoclinic unit cell with 10\%
-  water by weight (see Figure~\ref{fig:membrane_structure}). Approximately one
-  third of the water molecules occupy the tail region with the rest near the
-  pore center.
+  water by weight (see Figure~\ref{fig:membrane_structure}). 
+  % r1_comment4
+  Each unit cell contains $\sim$ 62,000 total atoms. 
+  Approximately one third of the water molecules occupy the tail region with
+  the rest near the pore center.
 %BJCC: I don't see a need to justify 10 over 5 wt% 
@@
 
+  \label{r1_comment2} % BJCR: description of force field.   
+  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
+  We used the antechamber module shipped with AmberTools18 to parameterize monomers and 
+  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
+  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
+  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
+  and was developed for consistency within the AMBER ecosystem, which used TIP3P as the
+  water model. We chose these standard force fields and generalizable parameterization 
+  approaches so that a range of solutes and monomers could be self-consistently and easily 
+  studied. The main goal of this work is to develop stochastic models which can reproduce
+  solute behavior on MD timescales, independent of the choice of force field. In future 
+  work, it may be beneficial to employ specialized force fields, including polarizable 
+  force fields or other higher-order effects in order to improve the accuracy of structure 
+  parameters and selectivity predictions.
+
   We chose to study a subset of the 4 fastest moving solutes from our previous
@@
   created a separate system and to each system we added 6 solutes per pore 
-  for a total of 24 solutes. On the time scales which we simulate, this number
+  for a total of 24 solutes. On the timescales which we simulate, this number
   of solutes per pore provides a sufficient amount of data from which to 
@@
 
-  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
+  We extended the 1 $\upmu$s simulations of our previous work to 5 $\upmu$s in order
   to collect ample data. We ran MD simulations using the leapfrog integrator with 
@@
 
+  % r1_comment3
+  Although we studied diffusion, we did not explicitly account for finite size effects
+  in this system. Finite size corrections to diffusion are primarily due to the
+  hydrodynamics of the surroundings~\cite{venable_lipid_2017,yeh_system-size_2004}, and
+  as discussed in our previous work~\cite{coscia_understanding_2019} the LLC membrane
+  (outside of intramolecular motion and quasiharmonic vibration around its average 
+  position) is mostly motionless, and therefore has a very high effective viscosity.
+  Nonetheless, studies of finite size effects in this system may be worthwhile in
+  future work. However, it likely would not affect the modeling approach described in
+  this work.
+
   \subsection{The Anomalous Diffusion Model}\label{method:model_sFBM}
 
-  On the time scales simulated in this study, solutes in this system very 
+  On the timescales simulated in this study, solutes in this system very 
   clearly exhibit subdiffusive behavior, a type of anomalous diffusion. 
@@
   \begin{equation}
-  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
+  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 \mathrm{d}t
   \label{eqn:tamsd}
   \end{equation}
-  where T is the length of the trajectory. In some situations, it may make
+  where $T$ is the length of the trajectory. In some situations, it may make
   more sense to use the ensemble MSD. We present further discussion of this
@@
 %  power law trapping behavior, the time between hops diverges so there is no 
-%  characteristic measurement time scale of solute motion. In fact, as measurement 
+%  characteristic measurement timescale of solute motion. In fact, as measurement 
 %  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
@@
 
-  One can characterize the CTRW component of an sFBM process by the parameters
-  which describe its dwell time and hop length distributions. We used the
-  \texttt{ruptures} Python package in order to automatically identify mean
-  shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018}
-  We used the corresponding hop lengths and dwell times between hops to
-  construct empirical distributions.
+  One can characterize the continuous time random walk component of a subordinated
+  fractional Brownian motion process by the parameters which describe its dwell 
+  time and hop length distributions. We used the \texttt{ruptures} Python package
+  in order to automatically identify mean shifts in solute trajectories, indicating
+  hops.\cite{truong_ruptures:_2018} We used the corresponding hop lengths and dwell
+  times between hops to construct empirical distributions.
 
@@
   to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model.
-  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the log 
-  likelihood function:~\cite{clauset_power-law_2009}
+  We determine maximum likelihood estimates of $\alpha$ and $\lambda$ by maximizing
+  the log likelihood function:~\cite{clauset_power-law_2009}
   \begin{equation}
@@
   \textit{Correlated hop length distributions:} The distribution of hop 
-  lengths by solutes undergoing an sFBM process is Gaussian, therefore we 
-  parameterize it by its standard deviation, $\sigma$.
-  ~\cite{metzler_random_2000, metzler_anomalous_2014,neusius_subdiffusion_2009}
+  lengths by solutes undergoing a subordinated fractional Brownian motion 
+  process is Gaussian, therefore we parameterize it by its standard deviation,
+  $\sigma$.~\cite{metzler_random_2000, metzler_anomalous_2014,neusius_subdiffusion_2009}
   The measured mean of the hop length distribution is always very close to zero so
@@
 
-  sFBM implies that hops are correlated which we describe using the Hurst
-  parameter, $H$. The autocovariance function of hop lengths has the
-  analytical form:~\cite{mandelbrot_fractional_1968}
+  Subordinate fractional Brownian motion implies that hops are correlated which 
+  we describe using the Hurst parameter, $H$. The autocovariance function of hop
+  lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
   \begin{equation}
@@
   \begin{equation}
-    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
+    p_{\alpha_h, \beta}(k;\upmu,\sigma) =\exp\left[i\upmu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
   \end{equation}
@@
   $\alpha_h$ is the index of stability or L\'evy index, $\beta$ is the skewness 
-  parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter. The most
+  parameter, $\upmu$ is the shift parameter and $\sigma$ is a scale parameter. The most
   familiar case, and one of three that can be expressed in terms of elementary functions,
   is the Gaussian PDF ($\alpha_h$ = 2, $\beta$ = 0). We assume symmetric distributions
-  centered about 0 implying that $\beta$ and $\mu$ are both 0.
+  centered about 0 implying that $\beta$ and $\upmu$ are both 0.
 
@@
   structure.~\cite{tikanmaki_fractional_2010} The autocovariance function for
-  FLM is:
+  fractional L\'evy motion is:
   \begin{equation}
@@
   Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
-  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
-  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
-  simulations illustrating this point.
+  from a L\'evy stable distribution results in the same autocorrelation structure as 
+  fractional Brownian motion. See Section~\ref{S-section:H_estimate} of the Supporting
+  Information for numerical simulations illustrating this point.
 
@@
   chosen from our bootstrapped parameter distributions. We propagated each
-  trajectory until the total time equaled or exceeded $T_{sim}~ \mu$s, then
+  trajectory until the total time equaled or exceeded $T_{sim}~ \upmu$s, then
   truncated the last data point so that the total time exactly equaled
-  $T_{sim}~ \mu$s since valid comparisons are only possible between fixed
+  $T_{sim}~ \upmu$s since valid comparisons are only possible between fixed
   length sFBM simulations.
@@
   We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
-  and AD model trajectories then estimated their uncertainty using statistical
-  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute
-  trajectories, where $n$ is the number of independent trajectories, with
-  replacement, from the ensemble of trajectories and then calculated the MSD of
-  the subset. We reported the time-averaged MSD up to a 1000 ns time lag with
-  corresponding 1$\sigma$ confidence intervals.
+  and stochastic anomalous diffusion trajectories and then estimated their 
+  uncertainty using statistical bootstrapping. For each bootstrap trial, we 
+  randomly chose $n$ solute trajectories, where $n$ is the number of independent
+  trajectories, with replacement, from the ensemble of trajectories and then 
+  calculated the MSD of the subset. We reported the time-averaged MSD up to a 
+  1000 ns time lag with corresponding 1$\sigma$ confidence intervals.
 
@@
 
-  We used the Python package \texttt{fbm}~\cite{flynn_exact_2019} to generate exact simulations of FBM
-  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
-  the Supporting Information) of the algorithm by Stoev and Taqqu to
-  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
-  are no known exact simulation algorithms for generating FLM trajectories.
+  We used the Python package \texttt{fbm}~\cite{flynn_exact_2019} to generate exact
+  simulations of fractional Brownian motion and our own Python implementation (see
+  Table~\ref{S-table:python_scripts} of the Supporting Information) of the algorithm
+  by Stoev and Taqqu to simulate fraction L\'evy motion.~\cite{stoev_simulation_2004}
+  Note that, to our knowledge, there are no known exact simulation algorithms for 
+  generating trajectories which exhibit fractional L\'evy motion.
   However, the algorithm we used sufficiently approximates draws from the
@@
 
-  A Markov state model (MSM) decomposes a time series into a set of discrete
+  A Markov state model decomposes a time series into a set of discrete
   states with transitions between states defined by a transition probability
@@
 
-  Adding to the standard MSM framework, we incorporated the dynamics of the
-  solutes within each state as well as the dynamics of state transitions, which
-  includes the overall configurational state of the solute and it's
-  environments. While MSMs are often used to estimate equilibrium populations
-  of various states, adding state-dependent dynamics allows us to simulate
-  solute trajectories. Hence why we refer to them as Markov state-dependent
+  Adding to the standard Markov state modeling framework, we incorporated the 
+  dynamics of the solutes within each state as well as the dynamics of state 
+  transitions, which includes the overall configurational state of the solute
+  and it's environments. While MSMs are often used to estimate equilibrium 
+  populations of various states, adding state-dependent dynamics allows us to
+  simulate solute trajectories. Hence why we refer to them as Markov state-dependent
   dynamical models (MSDDMs).
@@
 
-  We simulated realizations of the MSDDM using the probability transition
-  matrix and emission distributions. For each trajectory simulated, we chose an
-  initial state randomly from a uniform distribution. We generated a full state
-  sequence by randomly drawing subsequent states weighted by the rows of the
-  probability transition matrix corresponding to the particle's current state.
-  Again, because we are working with a finite data set, we incorporated
-  transition probability uncertainties into the rows of the transition matrix
-  by resampling them from a Dirichlet distribution. For each same-state
-  subsequence of the full state sequence, we simulated an FLM process using the
-  Hurst parameter of that state and the parameters of the corresponding
-  emission distribution. Independently, we simulated the transition between
-  each same-state sequence with an FLM process based on the Hurst parameter of
-  transition sequences and the parameters of the single transition emission
-  distribution. We used the same FLM simulation procedure described in
-  Section~\ref{method:model_sFBM}.
+  We simulated realizations of the Markov state-dependent dynamical model 
+  using the probability transition matrix and emission distributions. For each
+  trajectory simulated, we chose an initial state randomly from a uniform 
+  distribution. We generated a full state sequence by randomly drawing subsequent
+  states weighted by the rows of the probability transition matrix corresponding
+  to the particle's current state. Again, because we are working with a finite 
+  data set, we incorporated transition probability uncertainties into the rows 
+  of the transition matrix by resampling them from a Dirichlet distribution. For
+  each same-state subsequence of the full state sequence, we simulated a fractional
+  L\'evy motion process using the Hurst parameter of that state and the parameters 
+  of the corresponding emission distribution. Independently, we simulated the 
+  transition between each same-state sequence with an fractional L\'evy process 
+  based on the Hurst parameter of transition sequences and the parameters of the
+  single transition emission distribution. We used the same fractional L\'evy
+  motion simulation procedure described in Section~\ref{method:model_sFBM}.
 
@@
   pore of length $L$. For each pore length, we simulated 10,000 realizations
-  of an AD approach model
-  % and, due to 
-  %computational costs, 1,000 realizations of the MSDDM, 
-  all released at the pore entrance ($z=0$).  In the case of uncorrelated hops,
-  one can continuously draw from the hop length distribution until $z \geq L$
-  (or $-L$ for the sake of computational efficiency). The length of time
-  between the last time the particle crossed $z=0$ and the end of the
-  trajectory gives a single passage time. When particle hops are correlated, as
-  they are in all cases of this work, we cannot continuously construct the
-  particle trajectories. Rather, we must generate trajectories of length $n$
-  and measure the length of the sub-trajectory which traverses from $0$ to $L$
-  without becoming negative.
+  of an AD approach model all released at the pore entrance ($z=0$). In the 
+  case of uncorrelated hops, one can continuously draw from the hop length 
+  distribution until $z \geq L$ (or $-L$ for the sake of computational 
+  efficiency). The length of time between the last time the particle crossed 
+  $z=0$ and the end of the trajectory gives a single passage time. When particle
+  hops are correlated, as they are in all cases of this work, we cannot 
+  continuously construct the particle trajectories. Rather, we must generate 
+  trajectories of length $n$ and measure the length of the sub-trajectory which
+  traverses from $0$ to $L$ without becoming negative.
 
@@
   of entrapment. The near-Gaussian distribution of jump lengths and power law
-  distribution of dwell times are both characteristic of CTRWs
-  (See Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). 
+  distribution of dwell times are both characteristic of continuous time random
+  walks (see Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). 
   %The apparent
   Anti-correlation between hops suggests a fractional diffusion process is 
-  subordinate to the CTRW. Of the different models, a process subordinated by 
-  FBM or FLM is best supported by the data because the analytical correlation 
-  structures of hop lengths are close to those observed in our simulations 
-  (See Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information). Fractional 
-  motion is common in crowded viscoelastic environments where motion is highly
-  influenced by the movement of surrounding components, such as monomer tails 
-  in our case.~\cite{ernst_fractional_2012}
+  subordinate to the continuous time random walk. Of the different models, a 
+  process subordinated by fraction Brownian or L\'evy motion is best supported by 
+  the data because the analytical correlation structures of hop lengths are close
+  to those observed in our simulations (see Figure~\ref{S-fig:anticorrelated_hops}
+  of the Supporting Information). Fractional motion is common in crowded 
+  viscoelastic environments where motion is highly influenced by the movement of 
+  surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
 
@@
   \caption{Three representative trajectories generated from each solute exhibit hops
-	  between periods of entrapment, characteristic of a CTRW. Solute
-	  dynamics show radial dependence, represented by the color at each
-	  time point. The longest periods of entrapment typically occur when
+	  between periods of entrapment, characteristic of a continuous time random
+	  walk. Solute dynamics show radial dependence, represented by the color at 
+	  each time point. The longest periods of entrapment typically occur when
 	  solutes drift far from the pore center and into the tails.
@@
   to L\'evy stable distributions since it is more general than the Gaussian
-  distribution. We plotted the MLE fits of both on top of each solute's hop length
-  distribution in Figure~\ref{S-fig:anticorrelated_hops} of the
+  distribution. We plotted the maximum likelihood fits of both on top of each
+  solute's hop length distribution in Figure~\ref{S-fig:anticorrelated_hops} of the
   Supporting Information. The L\'evy distribution does a better job capturing
@@
   worthwhile. In fact, we typically observe very little difference between model
-  predictions parameterized with FLM versus FBM.% (see Figure~\ref{fig:anomalous_msds}).
+  predictions parameterized with fraction L\'evy versus Brownian motion.% (see Figure~\ref{fig:anomalous_msds}).
 
@@
   assumed pure power law behavior since it is consistent with most theoretical
-  descriptions of CTRWs. The data fits well to this model at short dwell times
-  but the density of long dwell times is over-estimated. In our second
-  approach, we truncate the power law distribution with an exponential cut-off,
-  lowering the probability of extremely long dwell times. 
+  descriptions of continuous time random walks. The data fits well to this model 
+  at short dwell times but the density of long dwell times is over-estimated.
+  In our second approach, we truncate the power law distribution with an exponential
+  cut-off, lowering the probability of extremely long dwell times. 
   %We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where 
-  On long time scales, the density of the truncated power law drops below that
+  On long timescales, the density of the truncated power law drops below that
   of the pure power law and tends towards 0. % near a dwell time of 250 ns.
 
-  Several of the choices of AD models and parameters we have described yield
-  qualitatively similar trajectories to those seen in our MD simulations.  In
-  Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for
-  each combination of the dwell time and hop distribution, labeled according to
-  Table~\ref{table:anomalous_models}. The sFBMcut and sFLMcut in particular
-  resemble the trajectories in Figure~\ref{fig:solute_trajectories}.  When we
-  do not truncate the dwell time distribution, the trajectories tend to
-  incorporate very long dwell times as shown by the sFBM and sFLM models.
+  Several of the choices of anomalous diffusion models and parameters we have
+  described yield qualitatively similar trajectories to those seen in our MD 
+  simulations. In Figure~\ref{fig:ad_eyetest}, we plot representative sample
+  trajectories for each combination of the dwell time and hop distribution, 
+  labeled according to Table~\ref{table:anomalous_models}. Subordinated fractional
+  Brownian and L\'evy motion trajectory realizations with dwell distributions 
+  truncated by an exponential function particularly resemble the trajectories in 
+  Figure~\ref{fig:solute_trajectories}. When we do not truncate the dwell time 
+  distribution, the trajectories tend to incorporate very long dwell times as shown
+  by the pure subordination fractional Brownian and L\'evy motion models.
   Predictions made with these models consistently under-predict the MD MSDs
   (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supporting Information).
-  Therefore, we will not include the pure sFBM or sFLM models in the
-  remainder of our analysis.
+  Therefore, we will only explore models with truncated dwell time distributions in
+  % not include the pure sFBM or sFLM models in the
+  the remainder of our analysis.
 
@@
   \caption{(a) Simulated urea trajectories generated by each of the four
-	  variations of the one mode AD model display qualitatively similar
-	  hopping and trapping behavior to that shown in
-	  Figure~\ref{fig:solute_trajectories}. Dwell times are exaggerated in
-	  the sFBM and sFLM models because the power law dwell time
+	  variations of the one mode anomalous diffusion model display qualitatively
+	  similar hopping and trapping behavior to that shown in 
+	  Figure~\ref{fig:solute_trajectories}. The abbreviations in this figure are
+	  defined in Table~\ref{table:anomalous_models}. Dwell times are exaggerated
+	  in the pure sFBM and sFLM models because the power law dwell time
 	  distributions are not truncated and have infinite variance. In (b)
@@
   We obtain reasonable predictions of the MD simulated MSDs when we
-  parameterize AD models with all available data after the perceived
-  equilibration time.   
+  parameterize anomalous diffusion models with all available data after 
+  the perceived equilibration time.
   %BJCB: added next two sentences point towards non-stationarity discussion
@@
   suggests that we may be operating on the border of the minimum amount of
-  data required to accurately parameterize AD approach models.
+  data required to accurately parameterize anomalous diffusion models.
   The MSD curves generated from both the one and two mode models are overlaid
@@
   \caption{In most cases, MSDs generated from realizations of both the one and
-	  two mode AD models lie within or near the 1$\sigma$ confidence
+	  two mode anomalous diffusion models lie within or near the 1$\sigma$ confidence
 	  intervals of MD-generated data. Drawing hops from a truncated L\'evy
@@
 
-  %MRS: some of these discussions might belong in the SI, with just the top line information in the main text.
-People don't really care about the details of the individual parameters, just what story that tells.
-  %BJCB: I think the figures need to stay though   
-  %MRSB: Hmm. I'm not entirely convinced, but we can leave it in for now and see what the reviewers think.
   \begin{figure}
@@
   \end{subfigure}
-  \caption{The parameters of the one mode model reveal differences in dynamics
-	  between solutes. (a) We parameterized Gaussian,
-	  $\mathcal{N}(\sigma)$, and L\'evy stable, $L(\sigma, \alpha_h)$,
-	  distributions to describe solute hop lengths. We assume the mean
-	  ($\mu$) to be zero for these distributions and no
-	  skewness ($\beta = 0$) in the L\'evy stable distributions. High
-	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
-	  hops. (b) We parameterized a pure power law, $P(\alpha)$, and a
-	  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe
-	  solute dwell times. Lower values of $\alpha$ lead to heavier power
-	  law tails and higher values of $\lambda$ truncate the distribution at
-	  lower dwell times. (c) Finally, we parameterized the hop
-	  autocorrelation function, $\gamma(H)$, to describe the degree of
-	  correlation between hops. Simulations with higher values of $H$ display
-	  behavior closer to the Brownian limit.}\label{fig:1mode_parameters}
+  \caption{% BJCR: r1_comment5. modified caption. Old caption commented out
+		  The parameters of the one mode model reveal differences in dynamics
+	      between solutes. (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, 
+	      and L\'evy stable, $L(\sigma, \alpha_h)$, distributions to describe
+	      solute hop lengths. Each bar represents the value of a single parameter,
+	      highlighted in bold, of the associated hop distribution. In general, 
+	      higher values of $\sigma$ and lower values of $\alpha_h$ result in 
+	      larger hops. (b) We parameterized a truncated power law distribution, 
+	      $P_T(\alpha, \lambda)$, to describe solute dwell times. Lower values
+	      of $\alpha$ lead to heavier power law tails and higher values of 
+	      $\lambda$ truncate the distribution at lower dwell times. (c) Finally,
+	      we parameterized the hop autocorrelation function, $\gamma(H)$, to 
+	      describe the degree of correlation between hops. Simulations with 
+	      higher values of $H$ display behavior closer to the Brownian limit.
+     % old caption
+%      The parameters of the one mode model reveal differences in dynamics
+%	  between solutes. (a) We parameterized Gaussian,
+%	  $\mathcal{N}(\sigma)$, and L\'evy stable, $L(\sigma, \alpha_h)$,
+%	  distributions to describe solute hop lengths. We assume the mean
+%	  ($\mu$) to be zero for these distributions and no
+%	  skewness ($\beta = 0$) in the L\'evy stable distributions. High
+%	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
+%	  hops. (b) We parameterized a pure power law, $P(\alpha)$, and a
+%	  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe
+%	  solute dwell times. Lower values of $\alpha$ lead to heavier power
+%	  law tails and higher values of $\lambda$ truncate the distribution at
+%	  lower dwell times. (c) Finally, we parameterized the hop
+%	  autocorrelation function, $\gamma(H)$, to describe the degree of
+%	  correlation between hops. Simulations with higher values of $H$ display
+%	  behavior closer to the Brownian limit.
+	  }\label{fig:1mode_parameters}
   \end{figure}
@@
   \end{subfigure}
-  \caption{The two mode model parameterizes solute behavior in the pore and tails
+  \caption{%BJCR: r1_comment5. modified caption - old caption commented out
+		  The two mode model parameterizes solute behavior in the pore and tails
 	      separately. We consider solutes to be within the pore region if they
 	      are 0.75 nm from a given pore center, otherwise they are in the
-	  tails. (a) Generally, movement is much more restricted in the tail
-	  region, parameterized by lower $\sigma$ values (smaller hops) for the
-	  Gaussian and L\'evy stable distributions. Values of $\alpha_h$ are
-	  significantly lower for urea and acetic acid meaning there is a
-	  larger probability that they will take large hops. (b) Dwell times
-	  are longer in the tails. Lower values of $\alpha$ correspond to power
-	  laws with heavier tails and thus higher probabilities of long dwell
-	  times. There is no easily discernible trend in $\lambda$ of the
+	      tails. For (a) and (b), each bar represents the value of a single parameter, 
+	      highlighted in bold, of the associated hop or dwell time distribution.
+	      Parameterizations of solute motion in the pores are visualized as bars
+	      in the upper half of the plots, while the parameters describing motion 
+	      in the tails are reflected into the lower half of the plots.
+	      (a) Generally, movement is more restricted in the tail region, but 
+	      with occasionally large hops, as implied by lower $\sigma$ (smaller
+	      hops) and $\alpha_h$ (heavier tails of the hop distribution) values.
+	      (b) Dwell times are longer in the tails as implied by lower values 
+	      of $\alpha$. There is no easily discernible trend in $\lambda$ of the
 	      truncated power law distribution. Note that we used the same Hurst
@@
 	      region dependent on their size, shape and chemical functionality.
-	  Methanol's small size favors occupation of the much larger accessible
-	  volume in the tails. Urea and acetic acid are fairly stable in both
-	  regions since they are small and hydrophilic. Ethylene glycol has a
-	  slight preference for the pores likely because it is a larger
-	  molecule with two hydrophilic hydroxyl groups.
+      % old caption
+%      The two mode model parameterizes solute behavior in the pore and tails
+%	  separately. We consider solutes to be within the pore region if they
+%	  are 0.75 nm from a given pore center, otherwise they are in the
+%	  tails. (a) Generally, movement is much more restricted in the tail
+%	  region, parameterized by lower $\sigma$ values (smaller hops) for the
+%	  Gaussian and L\'evy stable distributions. Values of $\alpha_h$ are
+%	  significantly lower for urea and acetic acid meaning there is a
+%	  larger probability that they will take large hops. (b) Dwell times
+%	  are longer in the tails. Lower values of $\alpha$ correspond to power
+%	  laws with heavier tails and thus higher probabilities of long dwell
+%	  times. There is no easily discernible trend in $\lambda$ of the
+%	  truncated power law distribution. Note that we used the same Hurst
+%	  parameter for both modes (shown in Figure~\ref{fig:hurst_barchart})
+%	  due to a low number of sufficiently long sequences of hops in each
+%	  mode. (c) Solutes spend various amounts of time in the tail and pore
+%	  region dependent on their size, shape and chemical functionality.
+%	  Methanol's small size favors occupation of the much larger accessible
+%	  volume in the tails. Urea and acetic acid are fairly stable in both
+%	  regions since they are small and hydrophilic. Ethylene glycol has a
+%	  slight preference for the pores likely because it is a larger
+%	  molecule with two hydrophilic hydroxyl groups.
   }\label{fig:2mode_parameters}
@@
   cases, both the Brownian (sFBMcut) and L\'evy (sFLMcut) versions of both the
-  one and two mode AD models give very similar results, 
+  one and two mode anomalous diffusion models give very similar results, 
   %most likely because
@@
 
-  % BJCB: I might be able to get away with moving this paragraph to SI if I briefly
-  % mention the reason in the above paragraph.
   The two mode models display curvature more consistent with MD but for
@@
   the width of the distribution used to model hops changes, and the correlation structure is broken. 
-  %MRSB: I cut below.
-  %We are unaware of
-  %an appropriate technique which can correlate hops that come from different
-  %hop distribution every time a mode switch occurs, the correlation
-  %structure is broken. 
   Solutes that switch between modes the least show
@@
 
-  Overall, the AD approach does a reasonable job of predicting solute MSDs and
+  Overall, the anomalous diffusion approach does a reasonable job of predicting solute MSDs and
   its parameters can help us further understand solute dynamics. Hops appear to
@@
 
-  The AD model is useful if one does not know exact transport mechanisms 
+  The anomalous diffusion model is useful if one does not know exact transport mechanisms 
   in a system since it only requires time series data. However, since we have
@@
   \caption{Solutes spend varying amounts of time under the influence of each
-	  trapping mechanism. To aid the reader, we labeled each state with an
+	  trapping mechanism. The state numbers correspond to those described in
+	  Table~\ref{table:states}. To aid the reader, we labeled each state with an
 	  abbreviation which identifies the combination of conditions to which
@@
   \end{figure}
-
-  % BJCB: I could summarize the four following paragraphs in terms of key
-  % takeaways, like you suggested with the AD model above.
 
@@
 
-  To create an MSDDM for each solute, we determined the state sequence associated
-  with each solute trajectory based on the geometric indicators of the states 
-  indicated in Table~\ref{table:states}. We then generated emission distributions of fluctuations
-  within each state as well as transitions between states. In theory, one could 
-  parameterize separate transition distributions for those which occur in the tails 
-  versus in the pores, however this would lead to a broken correlation structure 
-  similar to that seen in the two mode AD models.
+  To create a Markov state-dependent dynamical model for each solute, we determined
+  the state sequence associated with each solute trajectory based on the geometric 
+  indicators of the states defined in Table~\ref{table:states}. We then generated
+  emission distributions of fluctuations within each state as well as transitions 
+  between states. In theory, one could parameterize separate transition distributions
+  for those which occur in the tails versus in the pores, however this would lead to
+  a broken correlation structure similar to that seen in the two mode anomalous
+  diffusion models.
 
@@
 
-  %MRSB: discussion of parameter specifics is a potential place to move.
   \begin{figure}
@@
   \end{subfigure}
-  \caption{The parameters of the MSDDM are strong functions of trapping
-	  mechanisms. We observe different parameters but with similar trends
-	  between the tail and pore region. The states are defined in
-	  Table~\ref{table:states}. See Figure~\ref{fig:state_probabilities}
-	  for a description of the abbreviation under each state number. The
-	  legend in (a) applies to all subplots. (a) Motion is highly
-	  anti-correlated in trapped states. As the number of simultaneously
-	  influencing trapping mechanisms increases, the Hurst parameter, $H$,
-	  decreases. $H$ is highest (closest to Brownian) during transitions 
-	  between states (state T). (b) As more trapping mechanisms simultaneously influence solutes,
+  \caption{The parameters of the Markov state-dependent dynamical model
+      are strong functions of trapping mechanisms. We observe different 
+      parameters but with similar trends between the tail and pore region. 
+      The states are defined in Table~\ref{table:states}. See 
+      Figure~\ref{fig:state_probabilities} for a description of the 
+      abbreviation under each state number. The legend in (a) applies to
+      all subplots. (a) Motion is highly anti-correlated in trapped states. 
+      As the number of simultaneously influencing trapping mechanisms 
+      increases, the Hurst parameter, $H$, decreases. $H$ is highest 
+      (closest to Brownian) during transitions between states (state T). 
+      (b) As more trapping mechanisms simultaneously influence solutes,
 	  the width of the hop length distribution ($\sigma$) decreases. The
@@
   Quantitatively, the dynamics of urea, ethylene glycol and, to a lesser extent, 
-  methanol appear to be well-captured by the MSDDM. We simulated 1000 MSDDM trajectory realizations
-  for each solute, as described in Section~\ref{method:MSMs}, then calculated their
-  MSDs (see Figure~\ref{fig:msddm_performance}). In most cases, the MSDDM predicts
-  the magnitude of the MD MSDs within their 1$\sigma$ confidence intervals.
+  methanol appear to be well-captured by the Markov state-dependent dynamical 
+  model. We simulated 1000 MSDDM trajectory realizations for each solute, as 
+  described in Section~\ref{method:MSMs}, then calculated their MSDs (see 
+  Figure~\ref{fig:msddm_performance}). In most cases, the Markov state-dependent
+  dynamical model predicts the magnitude of the MD MSDs within their 1$\sigma$ 
+  confidence intervals.
 
@@
   predicted MSD actually lies just within the lower bound of urea's MD MSD
-  1$\sigma$ confidence interval, but lower than the prediction of the MSDDM for
-  urea. As stated earlier, most of a solute’s motion modeled by the MSDDM is
-  due to displacements during state transitions. Acetic acid has a transitional
-  Hurst parameter close to urea’s and transitional $\sigma$ and $\alpha_h$
-  values that are higher than urea’s. The primary reason that the MSDDM
-  predictions for acetic acid's MSD are lower than urea's appears to be because
-  of higher hop anti-correlation (lower $H$) in all states, including
-  transitions. There is also the strong possibility that the over-estimate is
-  a consequence of lumping together all of acetic acid’s transitional hops into
-  a single correlated distribution.
+  1$\sigma$ confidence interval, but lower than the prediction of the Markov 
+  state-dependent dynamical model for urea. As stated earlier, most of a solute’s
+  motion modeled by the MSDDM is due to displacements during state transitions.
+  Acetic acid has a transitional Hurst parameter close to urea’s and transitional
+  $\sigma$ and $\alpha_h$ values that are higher than urea’s. The primary reason 
+  that the Markov state-dependent dynamical model's predictions for acetic acid's
+  MSD are lower than urea's appears to be because of higher hop anti-correlation
+  (lower $H$) in all states, including transitions. There is also the strong 
+  possibility that the over-estimate is a consequence of lumping together all of
+  acetic acid’s transitional hops into a single correlated distribution.
 
@@
   \caption{In most cases, the magnitude of the MSD curves predicted by the
-	  MSDDM agree well with those generated from MD simulations. The
-	  predicted MSD curves of urea and ethylene glycol lie within the
-	  1$\sigma$ confidence intervals of MD for all time lags. Methanol
-	  over-predicts the MSD at small time lags and acetic acid grossly
-	  over-predicts the MSD at all time lags.  Like the AD approach models,
-	  the MSDDM doesn't fully capture the curvature of the MD MSD curves.
+	  Markov state-dependent dynamical model agree well with those generated 
+	  from MD simulations. The predicted MSD curves of urea and ethylene 
+	  glycol lie within the 1$\sigma$ confidence intervals of MD for all 
+	  time lags. Methanol over-predicts the MSD at small time lags and 
+	  acetic acid grossly over-predicts the MSD at all time lags.  Like the
+	  anomalous diffusion approach models, the Markov state-dependent dynamical
+	  model does not fully capture the curvature of the MD MSD curves.
 	  }\label{fig:msddm_performance}
@@
   Despite relatively good predictions of the MD MSD, qualitative mismatch
-  between simulated MSDDM and MD trajectories suggest that the MSDDM may be
-  getting the right answers for the wrong reasons. We plotted typical
-  realizations of the MSDDM for each solute and compared them to MD in
+  between stoachastic and MD simulated trajectories suggest that the Markov
+  state-dependent dynamical model may be giving the right answers for the
+  wrong reasons. We plotted typical realizations of the Markov state-dependent
+  dynamical model for each solute and compared them to MD in 
   Figure~\ref{fig:msddm_eyetest}. There is little evidence of trapping behavior
   or large hops. There are two reasons for this behavior. First, the width of
-  hop length distributions are much smaller than those of the AD model. Closer
-  examination of the characteristic MD trajectories shown in
+  hop length distributions are much smaller than those of the anomalous diffusion
+  model. Closer examination of the characteristic MD trajectories shown in
   Figure~\ref{fig:solute_trajectories} reveal that hops tend to be an
-  accumulation of a series of hops in the same direction. All of the hops in
-  the MSDDM are negatively correlated which prevents this from happening. The
-  second reason is a consequence of using a single hop length distribution for
-  transitions. This was necessary because we could not collect enough data to
-  fit all of the possible transition distributions and because we could not
-  correlate emissions coming from different hop distributions. Many
-  transitions occur between two trapped states where the transitional hops are
-  actually very small. Our model ignores this physical restriction which can
-  cause the solute to drift rather than stay trapped.
+  accumulation of a series of hops in the same direction. All of the hops generated
+  by the Markov state-dependent dynamical model are negatively correlated which
+  prevents this from happening. The second reason is a consequence of using a 
+  single hop length distribution for transitions. This was necessary because we 
+  could not collect enough data to fit all of the possible transition distributions
+  and because we could not correlate emissions coming from different hop 
+  distributions. Many transitions occur between two trapped states where the 
+  transitional hops are actually very small. Our model ignores this physical 
+  restriction which can cause the solute to drift rather than stay trapped.
 
@@
   \end{subfigure}
-  \caption{Realizations of the MSDDM for each solute (blue) do not reproduce
-	  the hopping and trapping behavior observed in our MD simulations
-	  (black). The trajectories are qualitatively similar to what one
-	  might expect for Brownian motion even though the MSDs are often similar
-	  to the atomistic systems.
+  \caption{Realizations of the Markov state-dependent dynamical model for 
+      each solute (blue) do not reproduce the hopping and trapping behavior 
+      observed in our MD simulations (black). The trajectories are 
+      qualitatively similar to what one might expect for Brownian motion 
+      even though the MSDs are often similar to the atomistic systems.
   	  }\label{fig:msddm_eyetest}
@@
 
-  We used the one mode sFBMcut (see Table~\ref{table:anomalous_models}) AD
-  model in order to demonstrate how one can use its realizations in order to
+  We used the truncated one mode subordinated fractional Brownian motion 
+  anomalous diffusion model (sFLMcut, see Table~\ref{table:anomalous_models})
+  in order to demonstrate how one can use its realizations in order to
   calculate the flux (see section~\ref{method:mfpt}) of solutes given model
-  parameters extracted from MD simulations. The one mode sFBMcut model
-  generates predictions similar to the one mode sFLMcut model at a lower
-  computational cost. We do not consider the two mode AD model because it has a
-  broken correlation structure and we do not consider the MSDDM because its
-  realizations do not display the expected hopping and trapping behavior.
+  parameters extracted from MD simulations. This model generates predictions 
+  comparable to the truncated one mode subordinated fractional L\'evy motion
+  anomalous diffusion model (sFLMcut) at a lower computational cost. 
+  % r1_comment8
+  Although it would be trivial to test the two mode anomalous diffusion models 
+  as well, we chose not to because we feel the results would be misleading to the
+  reader since the stochastic trajectories generated by this method lack a firm 
+  physical basis as discussed in Section~\ref{section:AD_all_data}. 
+  We also do not consider realizations of the Markov state-dependent dynamical 
+  model because its realizations do not display the expected hopping and 
+  trapping behavior.
+  %old text
+%  We do not consider the two mode AD model because it has a
+%  broken correlation structure and we do not consider the MSDDM because its
+%  realizations do not display the expected hopping and trapping behavior.
 
@@
   H\textsubscript{II} LLC membrane synthesized with the monomer in this work
-  was 7$\mu$m thick.~\cite{feng_thin_2016}
+  was 7$\upmu$m thick.~\cite{feng_thin_2016}
   Using 24 cores to simulate trajectory realizations in
   parallel, it takes on the order of 1 day to simulate 10000 sFBMcut
-  realizations of solutes traversing a 50 nm pore. The RAM requirements and
-  performance scales greater than linearly and thus would take an infeasible
-  amount of memory and time to simulate transport through a pore over 100 times
-  longer. One could improve performance significantly by simulating less
+  realizations of solutes traversing a 50 nm pore. 
+  % BJC: r1_comment9  
+  At this time, it is infeasible for us to simulate transport through a pore over 100 times 
+  longer without investing significant effort into writing and optimizing 
+  new code that can handle simulation of long trajectories with correlation
+  between all steps.
+  % old text
+%  The RAM requirements and
+%  performance scales greater than linearly and thus would take an infeasible
+%  amount of memory and time to simulate transport through a pore over 100 times
+%  longer. 
+  One could improve performance significantly by simulating less
   trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting
@@
 	  Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The
-	  single particle flux measured by the sFBMcut AD model decays with
-	  increasing pore length. The rankings of solute fluxes are consistent
+	  single particle flux measured by the sFBMcut anomalous diffusion model
+	  decays with increasing pore length. The rankings of solute fluxes are consistent
 	  with the MSDs predicted by each model. We fit the single particle
@@
 	  pore length. The strength of dependence on pore length depends on
-	  the difference between $\beta$ values. The largest differences in solute
-	  flux result in high selectivities at any pore length. This membrane
-	  may be a good candidate for the separation of ethylene glycol from
-	  acetic acid. Ethylene glycol has the lowest $\beta$ value while
-	  acetic acid has the second highest, leading to strong length
-	  dependence. Ethylene glycol also has the highest flux and acetic acid
-	  has the lowest resulting in relatively high selectivities independent
-	  of pore length.}
+ 	  the difference between $\beta$ values. 
+ 	  %BJCR: r1_comment5. removed redundant details
+%     The largest differences in solute
+%	  flux result in high selectivities at any pore length. This membrane
+%	  may be a good candidate for the separation of ethylene glycol from
+%	  acetic acid. Ethylene glycol has the lowest $\beta$ value while
+%	  acetic acid has the second highest, leading to strong length
+%	  dependence. Ethylene glycol also has the highest flux and acetic acid
+%	  has the lowest resulting in relatively high selectivities independent
+%	  of pore length.
+  }
   \label{fig:selectivity}
@@
 
-  We have tested two different mathematical frameworks for
-  %BJCA: rephrase
-  % describing solute motion
-  describing complex solute dynamics
-  by applying them to an H\textsubscript{II} phase LLC membrane. The
+  We have tested two different mathematical frameworks for describing complex
+  solute dynamics by applying them to an H\textsubscript{II} phase LLC membrane. The
   values obtained for the parameters when fitting the models to the time series
@@
   theoretical foundation in the anomalous diffusion literature. Our single mode
-  AD model quantifies and allows comparison of the hopping and trapping behavior
-  among solutes. A two mode model that describes dynamics based on whether a
-  solute is in or out of the pore region allows us to break down individual
-  solute motion into two distinct regimes and we showed that solute motion
-  is clearly restricted while in the tail region. Our Markov state-dependent
-  dynamical model uses explicitly defined trapping mechanisms and gives a nice
-  description of transitions between these observed states, the equilibrium
-  distribution of solutes among states as well as the type of stochastic
-  behavior shown in each state.
+  anomalous diffusion models quantify and allow comparison of the hopping and 
+  trapping behavior among solutes. A two mode anomalous diffusion model that 
+  describes dynamics based on whether a solute is in or out of the pore region
+  allows us to break down individual solute motion into two distinct regimes 
+  and we showed that solute motion is clearly restricted while in the tail 
+  region. Our Markov state-dependent dynamical model uses explicitly defined 
+  trapping mechanisms and gives a nice description of transitions between these 
+  observed states, the equilibrium distribution of solutes among states as well
+  as the type of stochastic behavior shown in each state.
 
@@
   within the 1$\sigma$ confidence intervals of MD, it is not always for
-  physically accurate reasons. Qualitatively, MSDDM trajectories do not display
-  the same hopping and trapping behavior shown by MD trajectories. Frequent
-  transitions drawn from a single, relatively broad transition emission
-  distribution prevent long periods of immobility. The most obvious solution to
-  this would be to generate individual emission distributions for each type of
-  transition, but this would require orders of magnitude more data or more
-  prior assumptions about the distributions. This approach is further
-  complicated by the need to make correlated draws from a fractional L\'evy
-  process with a frequently changing distribution width. A possible
-  simplification could be to assume that correlation is lost every time a state
-  transition occurs.
-
-  Although the AD approach generates qualitatively accurate trajectories and
-  predicts MSDs near or within the 1$\sigma$ confidence interval of our MD
-  simulations, the curvature of the predicted MSDs does not appear to be
-  consistent with the MD simulations. The MSD curves calculated from MD
-  simulations appear to straighten out on long timescales while those predicted
-  from the AD models continuously curve. This is because pure fractional Brownian motion
-  features hop correlation that persists indefinitely.
-  However, it is likely that on longer timescales, hops become decorrelated, 
-  causing solute dynamics to transition from subdiffusive to diffusive behavior.
-  We may be able to incorporate this transition by truncating the positional 
-  autocorrelation function, allowing correlation to diminish on the 100 ns 
-  time scale as suggested by the physical trajectories.
-
-  We demonstrated how one could use the one mode AD model,
-  %BJCA: added
-  or any stochastic time series model,
-  in order to to
-  determine macroscopic flux and selectivity. We showed that, when using the AD
-  model, solute flux decreases with pore length at a rate faster than pure
-  Brownian motion due to anti-correlation between hops.
-  % We used the ratio of
-  % solute fluxes generated from each model in order to calculate selectivity.
-  Due to differences in hop anti-correlation, we observe length dependent
-  selectivity. Based on these calculations we can hypothesize that this
-  particular LLC membrane may be a good candidate for the selective separation
-  of ethylene glycol from acetic acid or methanol.
+  physically accurate reasons. Qualitatively, trajectories generated by the 
+  Markov state-dependent dynamical model do not display the same hopping and 
+  trapping behavior shown by MD trajectories. Frequent transitions drawn from
+  a single, relatively broad transition emission distribution prevent long
+  periods of immobility. The most obvious solution to this would be to generate
+  individual emission distributions for each type of transition, but this would
+  require orders of magnitude more data or more prior assumptions about the 
+  distributions. This approach is further complicated by the need to make 
+  correlated draws from a fractional L\'evy process with a frequently changing
+  distribution width. A possible simplification could be to assume that 
+  correlation is lost every time a state transition occurs.
+
+  Although the anomalous diffusion approach generates qualitatively accurate 
+  trajectories and predicts MSDs near or within the 1$\sigma$ confidence 
+  interval of our MD simulations, the curvature of the predicted MSDs does not
+  appear to be consistent with the MD simulations. The MSD curves calculated 
+  from MD simulations appear to straighten out on long timescales while those 
+  predicted from the anomalous diffusion models continuously curve. This is 
+  because pure fractional Brownian motion features hop correlation that persists
+  indefinitely. However, it is likely that on longer timescales, hops become
+  decorrelated, causing solute dynamics to transition from subdiffusive to 
+  diffusive behavior. We may be able to incorporate this transition by 
+  truncating the positional autocorrelation function, allowing correlation to
+  diminish on the 100 ns timescale as suggested by the physical trajectories.
+
+  We demonstrated how one could use the one mode anomalous diffusion model, and
+  in turn any stochastic time series model, in order to to determine macroscopic
+  flux and selectivity. We showed that, when using the anomalous diffusion model,
+  solute flux decreases with pore length at a rate faster than pure Brownian 
+  motion due to anti-correlation between hops. Due to differences in hop 
+  anti-correlation, we observe length dependent selectivity. Based on these 
+  calculations we can hypothesize that this particular LLC membrane may be a good
+  candidate for the selective separation of ethylene glycol from acetic acid or methanol.
 
@@
 
-  \section*{Supporting Information}
-
-  Detailed explanations and expansions upon the results and procedures
-  mentioned in the main text are described in the Supporting Information. This
-  information is available free of charge via the Internet at
-  http://pubs.acs.org.
-
   \section*{Acknowledgments}
@@
   University of Colorado Boulder and Colorado State University.
+
+  \section*{Supporting Information}
+
+  Detailed explanations and expansions upon the results and procedures
+  mentioned in the main text are described in the Supporting Information. This
+  information is available free of charge via the Internet at
+  http://pubs.acs.org.
 

### 2020-07-13 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex
minor comments in.

@@
   We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
-  We used the antechamber module shipped with AmberTools18 to parameterize monomers and 
+  We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
   solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
@@
   GAFF is very commonly used in simulations with diverse organic chemical functionality, 
-  and was developed for consistency within the AMBER ecosystem, which used TIP3P as the
+  and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
   water model. We chose these standard force fields and generalizable parameterization 
@@
 		before fitting them to Equation 9. This is especially challenging with slow-moving solutes
-		like acetic acid. We needed to simulate over 2 million timesteps in order to sufficiently
+		like acetic acid. We needed to simulate over 2 million time steps in order to sufficiently
 		sample the MFPT over a 50 nm pore. This procedure becomes computationally expensive very
@@
 
+	  	%MRS: scanning over this, it's probably more important to say that we probably didn't need to do it, since
+                %the analytical fit was so good.
 	  	Modified text:
@@
 \end{document}
+
+% LocalWords:  Subdiffusive Solute Nanoscale Coscia leftmargin FBM vy
+% LocalWords:  subdiffusion CTRW sFBM ref solutes antechamber solute
+% LocalWords:  polarizable LLC intramolecular quasiharmonic BJC JCTC
+% LocalWords:  tex fontsize evy Methanol's selectivities MSDDM arXiv
+% LocalWords:  parametrization MSDs MSD timescales renormalizing MFPT
+% LocalWords:  bicontinuous Donnan steric em dt lyotropic
+% LocalWords:  subdiffusive

### 2020-08-01 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
Started response to reviewers for hdphmm

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{xr}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{scrextend}
\usepackage[normalem]{ulem}

\externaldocument[S-]{Supporting_Information}
\externaldocument[M-]{Final_Draft}

\begin{document}

\graphicspath{{./figures/}}

\begin{center}
\textbf{Response to reviewers: Statistical Inference of Transport Mechanisms and Long
        Time Scale Behavior from Time Series of Solute Trajectories in Nanostructured Membranes} \\
Authors: Benjamin J. Coscia, Christopher P. Calderon and Michael R. Shirts
\end{center}

We thank the reviewers for carefully reading over our manuscript and providing
thoughtful and constructive feedback. We have taken the suggestions into consideration 
and made appropriate revisions to the manuscript document. The comments have been reproduced
in italics and all changes to the text have been documented below them. Any newly added
references are given in the bibliography of this document and are placed in the main 
text with appropriate numbering.

\section*{Response to Reviewer 1}

\begin{enumerate}[label={Comment \theenumi :}, leftmargin=3.9\parindent]

    \item \textit{The manuscript by Coscia et al. analyzes diffusion and transport of solute molecules
    in a low water content lyotropic liquid crystal using a statistical model developed on the basis 
    of molecular dynamics simulations. The purpose of the statistical model is two-fold; first to 
    extrapolate computed MSDs to longer times to obtain diffusion coefficients, and second to attempt
    to gain increased physical insight on diffusion mechanisms. These issues are important in 
    highly-confined/low-water content nanoporous materials, in which diffusion occurs through complex
    mechanisms and over long timescales. The manuscript will most likely be of interest to the community
    interested in nanoporous materials for separations.}

    Author reply:

    \item \textit {Unfortunately, because there is no comparison with alternative techniques, it is 
    very difficult to evaluate this new approach relative to previous work that has examined similar 
    issues. There exist numerous other methods for extrapolating MSDs to longer time, which the 
    authors have not discussed. One such method is the “trajectory-extending kinetic Monte Carlo” 
    (TEKMC) approach of Brown and coworkers see e.g. Macromolecules 2010, 43, 9210-9214, 
    Macromolecules 2015, 48, 7346-7358, and J. Phys Chem. B, 2012, 116, 95-103. The authors should 
    add a comprehensive discussion of how their approach compares to this and similar methods. The 
    paper would be significantly improved if the authors were to perform and present TEKMC results 
    for their system, so that one could better evaluate the performance of their proposed method.}

    Author reply:

    %BJC: not sure if I should ignore the JCTC part completely or basically just say what the editor said.
    \item \textit{Much of the writing seems more suitable for JCTC rather than JPC. I encourage the
    authors to better emphasize and discuss “new physical insight” and “chemical details”, and spend
    less time on methodology. For example pages 5-16 are all on methodology, yet it is not until 
    Figure 8 of the paper (page 26) that the authors give any description of what the LLC system 
    they are studying is actually composed of. Presumably the LLC is made up of self-assembled 
    monomers (in water) shown in Figure 8a). I would encourage the authors to describe their 
    system more concretely much earlier in the paper... there is also no information on system 
    size, box dimensions, etc.}

    Author reply: We thank the reviewer for pushing us to include more details about our 
  molecular simulations in order to boost reproducibility. The length of the manuscript made
  us wary to include information that could be accessed elsewhere, however there are 
  benefits to keep this very important section self-contained.

  We added the following text to address comments related to our choice of force field:

  New text:
  \begin{quote}
  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
  We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
  and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
  water model. We chose these standard force fields and generalizable parameterization 
  approaches so that a range of solutes and monomers could be self-consistently and easily 
  studied. The main goal of this work is to develop stochastic models which can reproduce
  solute behavior on MD time scales, independent of the choice of force field. In future 
  work, it may be beneficial to employ specialized force fields, including polarizable 
  force fields or other higher-order effects in order to improve the accuracy of structure 
  parameters and selectivity predictions.
  \end{quote}

  % comment 4      
  \item \textit{Lastly, it would be natural to report the size of the system in this
              section (I found it eventually in the introduction after searching for it 
              throughout the manuscript).}

              Author reply:

              We thank the reviewer for pointing out this missing piece of information. We
              have added the following text in order to inform the reader of the system's size:
			  \begin{quote} 
			  Each unit cell contains $\sim$ 62,000 total atoms.
			  \end{quote}

    Author reply:

    \item \textit{The authors should more clearly note that their discussion largely applies only 
    to very low water content LLC regimes (such as the 10\% LLC studied). For higher water content 
    LLCs (e.g. > 15-20\%) it is straightforward to obtain the diffusion limit from standard MD 
    simulations. While the authors are surely well aware of this, the reader may not be, and it is
    important to clearly distinguish the regimes.}

    \item \textit{In the HDP-AR-HMM method, it is not clear to me how the solute molecules are 
    constrained to be confined within the pore radius (which they must be on physical grounds 
    based on steric interactions). From Figure 2, it “looks” like this happens to work out, but
    for more complicated systems (e.g. gyroid LLCs with 3D channels) such a constraint may be 
    necessary and it is unclear how the method would generalize. This should be discussed.}

    \item \textit{As stated in the introduction, one motivation for the work is that “...one 
    cannot reliably compute diffusion constants because MSDs are often non-linear on the timescales
    accessible to molecular simulation”. Later on in section 2.4, the authors state “For the 
    purposes of our analysis, we assume ergodicity of the 24 solute trajectories.” These are 
    contradictory statements. If the trajectories are ergodic, then MSDs will be linear by 
    definition The authors should clarify. Similarly, in Figure 7, if the simulations are indeed 
    ergodic the red and blue bars should be proportional to each other.}

    \item \textit{There are no units on Figure 1 y-axis, presumably these are nanometer like the 
    other figures?}

    \item \textit{Figure captions need to be improved. Wording such as “we plotted...”, “we 
    calculated...”, “We also analyzed...” should be omitted in figure captions.}

%  Original text:
%  \begin{quote}
%  We treat our system in terms of two well-known classes of anomalous subdiffusion: 
%  \end{quote}
%  
%  New text:
%  \begin{quote}
%  In this first approach, we treat our system in terms of two well-known types of molecular
%  motion which lead to anomalous subdiffusion: 
%  \end{quote}

  \end{enumerate}

\section*{Response to Reviewer 2}

\begin{enumerate}[label={Comment \theenumi :}, leftmargin=3.9\parindent]

    %r2_comment1
    \item \textit{This paper presents an approach to study transport mechanisms of solutes within
    membranes by applying the sticky hierarchical Dirichlet process autoregressive hidden Markov model
    (HDP-AR-HMM) to molecular dynamics simulation trajectories spanning long times (5 microseconds). 
    Using this method, the authors reveal different dynamic states associated with the transport of 
    solute across a membrane, and interpret them on the basis of solute-membrane interactions. The 
    paper is clear, well written, and relevant to the Journal of Physical Chemistry. I only have a 
    couple of suggestions and minor corrections:}

    Author reply: We thank the reviewer for their kind assessment of our work.

    %r2_comment2
    \item \textit{A motivation for the study is providing a computational tool to guide experimentalists
    in designing membrane materials. However, given the length of the molecular dynamics simulations 
    required, it is presumably impractical to carry a large-scale screening in this way. It would be 
    useful if the authors were more explicit about the role of this approach in guiding experiments, 
    and what would be its advantages and limitations compared to a purely experimental search.}

    Author reply: We thank the reviewer for pushing us to further evaluate the practicality of our
    method as a tool for experimentalists. In short, there are many ways we can envision that 
    would make this approach more amenable to high throughput simulations. The length of our 
    simulations in this paper are indeed quite long. The dynamics of the solutes are somewhat 
    slow and we wanted to ensure we gathered enough data for a sufficient parameterization. 
    Putting aside brute force high throughput simulations that could be enabled by the 
    ever-increasing availability of HPC resources, it would be to our benefit to use the system
    in this work as a benchmark to explore much less expensive models.
    %BJC: I'm not exactly sure where to put this. Originally I thought conclusions because it's
    %not really a method, but seemed to make the most sense near the system description.
    We propose some ideas to this end in the text we have added to the end of Section 2.1, where
    our simulations are described:
    \begin{quote}
    In consideration of our ultimate goal, which is to use high-throughput simulations to 
    facilitate our understanding of LLC membrane design for solute-specific separations, the size 
    of our system and length of the accompanying molecular simulations appears to be somewhat 
    impractical. We would like to emphasize that our large, fully atomistic models will be
    extremely valuable as a benchmark systems used to explore less expensive models. For example, we 
    could explore systems built with fewer LLC monomers by making the membrane pores shorter. We 
    could also build systems with higher concentrations of solutes in order to gather more 
    dynamical data on shorter timescales. Using what we have learned about the radial distribution
    functions of these solutes in this and our previous work\cite{}, it may be possible to 
    learn how to create initial configurations with solutes initially distributed in a way that
    is close to their equilibrium distribution, allowing solutes to thoroughly explore the 
    accessible membrane structural space more quickly and reducing the amount unequilibrated
    data that must be discarded. % could mention GCMC?
    Finally, it may be possible to speed up our simulations by 
    reducing the number of atoms using united-atom representations of the liquid crystal monomers.
    %BJC: How strong of an influence would hydrogen mass repartitioning have on hydrogen bonding?
    %, or by using hydrogen mass repartitioning to allow us to increase the MD time step.

    \end{quote}

    %r2_comment3
    \item \textit{Have the authors attempted to compare their results directly to experimental data? 
    It would be useful to clarify whether the predicted selectivities are expected to be quantitatively
    accurate or just reflect trends.}

    %BJC: This is copied straight from the reviewer response for the previous paper.
    Author reply: The reviewer makes a valid point. This work started in parallel with experimental
    work which promised solute flux and selectivities that we could compare directly to our
	simulations. However, synthesizing an aligned hexagonal phase membrane has been a practical
	challenge for our experimental collaborators and much of their focus has shifted to 
	membranes formed by liquid crystals that self-assemble into bicontinuous cubic architectures
	which are much simpler to synthesize. We have also started to shift our focus towards models 
	of the bicontinuous cubic phase, which do have much more experimental data. However, our 
	research into generating physically accurate molecular models of that phase lags our work on
	time series modeling. In future work, we will be able to apply this technique to these 
	bicontinuous systems for which we have experimental data.

    %r2_comment4    
    \item \textit{As two very minor corrections, in page 15 line 8 it should say "Method 1", and in 
    page 17 line 5 the angle should be H-D-A.}

    % BJC: reviewer is right, VMD docs are misleading: https://www.ks.uiuc.edu/Research/vmd/plugins/hbonds/
    Author reply: We thank the reviewer for pointing out our potential errors. For the hydrogen bond
    criteria we have updated the text from "D-H-A" to "H-D-A". Regarding page 15 line 8 (\textit{"Method 2:
    Since trajectories generated by Method 2..."}), changing "Method 2" to "Method 1" would actually be 
    incorrect. At the beginning of Section 2.4, we defined two techniques for generating stochastic 
    trajectories. 'Method 2' on page 15 line 8 describes the bootstrapping procedures for Method 2 of
    trajectory generation. This is a clear lack of clarity on the author's part and therefore we 
    have made an effort to avoid to change our wording to avoid confusion.

    First, we added additional clarification before describing the bootstrapping procedure (added text
    is highlighted in red):
    \begin{quote}
    Our bootstrapping procedure varied dependent on the method of trajectory generation. \textcolor{red}{
    The following procedures correspond to the methods described above:}
    \end{quote}

    We have also modified the text on page 15 line 8 from the orginal text:
    \begin{quote}
    Since trajectories generated by Method 2 are based on the clustered parameter set used to define a
    single model, we can bootstrap on trajectory ensembles of arbitrary size.
    \end{quote}
    to:
    \begin{quote}
    Since in our second approach to stochastic trajectory generation described above we use clustered 
    parameter sets to define each model, we can bootstrap on trajectory ensembles of arbitrary size.
    \end{quote}

\end{enumerate}

\bibliographystyle{ieeetr}
\bibliography{stochastic_transport}

\end{document}

% LocalWords:  Subdiffusive Solute Nanoscale Coscia leftmargin FBM vy
% LocalWords:  subdiffusion CTRW sFBM ref solutes antechamber solute
% LocalWords:  polarizable LLC intramolecular quasiharmonic BJC JCTC
% LocalWords:  tex fontsize evy Methanol's selectivities MSDDM arXiv
% LocalWords:  parametrization MSDs MSD timescales renormalizing MFPT
% LocalWords:  bicontinuous Donnan steric em dt lyotropic
% LocalWords:  subdiffusive

### 2020-08-01 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex
Small edits
Started response to reviewers for hdphmm

@@
 		The reviewer is correct in their interpretation of the figures. For clarity, we modified the y-axes as
-		well as the caption in order to further aid the reader in reading them. We also made efforts to cut
+		well as the captions in order to further aid the reader in reading them. We also made efforts to cut
         down on the interpretation that is already presented in the main text. We made similar modifications
@@
         we feel the results would be misleading to the reader since the stochastic trajectories
-        generated by this method lack a firm physical basis as discussed in Section~\ref{M-section:AD_all_data}. 
+        generated by this method lack a firm physical basis as discussed in Section 3.1.2. 
         We also do not consider the MSDDM because its realizations do not display the expected 
@@
 	  	handle simulation of large trajectories with correlation between all steps. 
+        %BJC: added	  	
+	  	However, the high quality of our fits suggests that additional effort on this front may be
+	  	misplaced at this time. 
 	  	\end{quote}
@@
 	We thank the reviewer for their constructive feedback. In response we have reduced our usage of
-	acronyms for the various stochastic models in favor of their full unabbreviated form for clarity.
+	acronyms for the various stochastic models in favor of their full unabbreviated form for clarity. \\
 
@@
     \begin{quote}
-    The complex membrane topology (see~\ref{M-fig:membrane_structure}) gives rise to
+    The complex membrane topology (see Figure~\ref{M-fig:membrane_structure}) gives rise to
     three mechanisms responsible for the solute trapping behavior: 

### 2020-08-01 Ben_Manuscripts/hdphmm/Draft.tex
Started response to reviewers for hdphmm

@@
   results of 200 bootstrap trials. Our bootstrapping procedure varied dependent on the
-  method of trajectory generation:
-  %MRS: this is a bit confusing.  Is there an expectation these should give consistent parameters?
-  %MRS: the second is boostrapping an MSD over 1000 trajectories, and the first is boostrapping an MSD over 24 trajectories.
-  %MRS: these should have different amounts of noise, making them hard to compare? Is this an issue?
-  %BJC: added some clarification to Method 2
+  method of trajectory generation. The following procedures correspond to the methods
+  described at the beginning of this section:
   \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
@@
     constituting the bootstrapped ensemble.
-    \item Since trajectories generated by Method 2 are based on the clustered parameter 
-    set used to define a single model, we can bootstrap on trajectory ensembles of
-    arbitrary size. For each bootstrap trial, we generated an ensemble of 1000 independent
+    %r2_comment4
+    \item Since in our second approach to stochastic trajectory generation described 
+    above we use clustered parameter sets to define each model, we can bootstrap on 
+    trajectory ensembles of arbitrary size. 
+%    \item Since trajectories generated by Method 2 are based on the clustered parameter 
+%    set used to define a single model, we can bootstrap on trajectory ensembles of
+%    arbitrary size. 
+    For each bootstrap trial, we generated an ensemble of 1000 independent
     stochastic trajectories, calculated the MSD of each and then sampled, with replacement,
@@
   if the distance between donor, D, and acceptor, A, atoms is less than 
-  3.5\AA~and the angle formed by $D-H \cdots A$ is less than $30\degree$.~\cite{luzar_effect_1996}
+  3.5\AA~and the angle formed by $H-D-A$ is less than $30\degree$.~\cite{luzar_effect_1996}
 

### 2020-08-02 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
Near-complete draft of reviewer responses

@@
 \usepackage[normalem]{ulem}
+\usepackage{soul}
 
@@
 
+    %r1_comment1
     \item \textit{The manuscript by Coscia et al. analyzes diffusion and transport of solute molecules
@@
 
-    Author reply:
+    Author reply: We thank the reviewer for their thoughtful assessment of our work.
 
+    %r1_comment2
     \item \textit {Unfortunately, because there is no comparison with alternative techniques, it is 
@@
     Macromolecules 2015, 48, 7346-7358, and J. Phys Chem. B, 2012, 116, 95-103. The authors should 
+    %BJC: well Venkat Ganesan just relinquished his anonymity
     add a comprehensive discussion of how their approach compares to this and similar methods. The 
@@
 
-    Author reply:
+    Author reply: We thank the reviewer for bringing our attention to these other interesting 
+    approaches. They certainly merit discussion as alternative approaches for measuring diffusivity
+    and selectivity. We have added some discussion of these methods to the introduction.
 
+    \begin{quote}
+    TBD
+    \end{quote}
+
+    We agree that a full comparison of our method to other methods for computing long timescale 
+    diffusion such as TEKMC would be very interesting and instructive but feel it would be better 
+    suited as a separate study where we could include a number of approaches, including perhaps
+    recent approaches we have developed within our research group.~\cite{} We would also prefer to have
+    sufficient time to appropriately implement the technique for our system. Although it seems a
+    fairly straightforward approach to implement, it is not immediately clear how we could
+    optimally adapt the methodology to a monoclinic unit cell with two dimensional order. 
+%    the grids that divide the homogeneous cubic unit cells of the referenced TEKMC studies to 
+%    our system which uses a monoclinic unit cell and has 2 dimensional order.
+
+    As stated by the reviewer, there are two goals of our work: to obtain long timescale MSDs and
+    to understand mechanisms leading to diffusive behavior. TEKMC may be a suitable alternative 
+    approach to obtaining our first goal, but it is not clear that it could give the same level
+    of mechanistic insight that the HDP-AR-HMM offers. Although the work by Hansen et al.
+    (J. Phys Chem. B, 2012, 116, 95-103) is able to provide physical insight into the effect of
+    nanoparticles on diffusion of gaseous penetrants in a polystyrene polymer matrix, it does so
+    by testing hypotheses motivated by observations of the diffusion constant (predicted by TEKMC)
+    in response to different temperatures and nanoparticle concentrations. This is actually pretty
+    in line with the type of analysis we performed in our initial LLC work where we used the
+    mean squared displacement and the qualitative characteristic of the solute time series in
+    order to hypothesize transport mechanisms. In this work we "re-discover" these mechanisms
+    and characterize them in detail using the HDP-AR-HMM while simultaneously providing a method 
+    to estimate diffusion constants.
+
+    %r1_comment3
     %BJC: not sure if I should ignore the JCTC part completely or basically just say what the editor said.
@@
 
-    Author reply: We thank the reviewer for pushing us to include more details about our 
-  molecular simulations in order to boost reproducibility. The length of the manuscript made
-  us wary to include information that could be accessed elsewhere, however there are 
-  benefits to keep this very important section self-contained.
+    Author reply: We thank the reviewer for encouraging us to include more physical insight and
+    further details about our molecular simulations. Regarding physical insight, it is our 
+    understanding that the scope of JPC has been expanded to welcome papers which focus on 
+    methodology. We have studied the structure of and transport within this particular LLC system
+    extensively in our previous work.\cite{} We feel strongly that our current work should 
+    emphasize the HDP-AR-HMM as a more general tool for understanding complex dynamics in 
+    systems beyond our example system. We would prefer not to cut any methodological details, as
+    this would hurt the paper's reproducibilty, and lengthening the paper by including additional
+    physical insight may narrow the audience willing to dive in.
 
-  We added the following text to address comments related to our choice of force field:
+    %BJC: probably could add a picture of the system. Or is it okay to just reference another
+    % paper? I would probably use the same pic anyways or something very similar.
 
-  New text:
+    We do agree that there are certain basic simulation details that we have neglected to 
+    mention. Therefore we have made the following edits to section 2.1 of the methods:
+
+    We added the highlight text to the first sentence of the section:
     \begin{quote}
+      We studied transport of solutes in the H\textsubscript{II} phase using an atomistic 
+      molecular model of four pores in a monoclinic unit cell with 10\% water by weight, 
+      \hl{totaling 62,000 atoms}.    
+    \end{quote}
+
+    We have also added the following text describing the model: %BJC: not actually added yet
+    \begin{quote}
+    %BJC: this is verbatim from last response to reviewers.
     We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
@@
 
-  % comment 4      
-  \item \textit{Lastly, it would be natural to report the size of the system in this
-              section (I found it eventually in the introduction after searching for it 
-              throughout the manuscript).}
-
-              Author reply:
-
-              We thank the reviewer for pointing out this missing piece of information. We
-              have added the following text in order to inform the reader of the system's size:
-			  \begin{quote} 
-			  Each unit cell contains $\sim$ 62,000 total atoms.
-			  \end{quote}
-
-    Author reply:
-
+    %r1_comment4
     \item \textit{The authors should more clearly note that their discussion largely applies only 
@@
 
+    Author reply: We thank the reviewer for making this point. In higher water content systems, 
+    the time scales necessary to reach a diffusive regime will be much more attainable with 
+    standard MD. However, we do contend that our method would still be very useful for studying
+    solute dynamics in these higher water content systems. Interactions characterized by different
+    dynamical behavior even on short time scales can still be highly informative. This is the
+    basis for the point we make in the introduction: "...direct calculations of diffusion 
+    constants may obscure the molecular mechanisms controlling transport". Therefore we would
+    prefer not to limit the range of application of this method. 
+    %BJC: could add something to the effect. If you only care about diffusivity, then this level of modeling isn't necessary in many systems.
+
+    %r1_comment5
     \item \textit{In the HDP-AR-HMM method, it is not clear to me how the solute molecules are 
@@
 
+    Author reply: We thank the reviewer for posing this question as this a constraint to which 
+    we gave thought but neglected to emphasize in the main text. 
+    %BJC: he's not saying that solutes should stay in the aqueous pore region right? We talk pretty
+    % extensively about solute behavior in the tails so his steric argument is confusing me.  
+%    First, we would like to clarify
+%    that our simulations suggest that small solutes can partition out of the pores and into
+%    the dense tail region. This is not a particularly favorable move as evidenced by our radial
+%    distribution functions, but it does happen and could conceivably lead to rare jumps of solutes
+%    between pores (although we have not observed any).
+    The constraint on our stochastic simulations is built into the trajectory generation procedure.
+    Each state is parameterized by a mean in the radial direction computed based on the solute's 
+    distance from the \textit{nearest pore center}, making it impossible for the solute to get 
+    further than the pore radius away. Each time a state change occurs, the mean position of the
+    solute in the $r$ dimension jumps to the appropriate mean. However, in the axial direction, 
+    we do not parameterize the mean since it should be unbounded in that dimension. The $z$ mean
+    of each segment is set based on the position immediately before the state change occurred.
+
+    The generalization of this procedure to three dimensions will be under active investigation 
+    in the near future. As mentioned, we are interested in applying this approach to bicontinuous
+    cubic phases like the gyroid. Based on our current understanding, we would model solute dynamics
+    in three dimensions and set the mean vector, $\mathbf{c}$ equal to $\mathbf{0}$. Of course, this
+    may result in solutes exploring a three dimensional shape that does not share the geometric 
+    features of the studied phase. Our hypothesis is that we can add one or more additional 
+    dimensions to the time series passed to the HDP-AR-HMM that includes a distance from the pore centers. 
+    We could define the pore center using a spline or a surface and transitions would likely
+    favor moves towards states that exist closer to the pore interiors. Alternatively, it may prove
+    necessary to constrain solute positions to the means in each dimension. However, this would require 
+    much more data and would likely require us to explore less expensive models as described in
+    the response to Reviewer 2 below.
+
+    %r1_comment6
     \item \textit{As stated in the introduction, one motivation for the work is that “...one 
@@
 
+    Author reply: We thank the reviewer for identifying the potential confusion that could be
+    caused by our use of the word 'ergodic'. Figure 7 clearly demonstrates that individual trajectories
+    are not by themselves ergodic. Our intention was to communicate our assumption that all 24 
+    trajectories visit all possible dynamic states with representative probability. This is 
+    necessary in order to make accurate long timescale predictions. The 5 $\mu_s$ length of our 
+    simulations was intended to increase the validity of this assumption.
+
+    The use of the word 'ergodic' is not necessary, therefore we have modified the text as follow
+    to remove the source of miscommunication:
+
+    %r1_comment7
+    \begin{quote}
+    For the purposes of our analysis, \sout{we assume ergodicity of the 24 solute trajectories. That is,}
+    we assume our MD simulations sample all possible states with the correct frequency.
+    \end{quote}
+
     \item \textit{There are no units on Figure 1 y-axis, presumably these are nanometer like the 
@@
 
+    Author reply: We thank the reviewer for catching our oversight. We double-checked the 
+    other plots in the paper and found the same mistake on the y-axes of Figure 5. Units of nanometers
+    have been added to the y-axes of both plots.
+
+    %r1_comment8
     \item \textit{Figure captions need to be improved. Wording such as “we plotted...”, “we 
     calculated...”, “We also analyzed...” should be omitted in figure captions.}  
-
-%  Original text:
-%  \begin{quote}
-%  We treat our system in terms of two well-known classes of anomalous subdiffusion: 
-%  \end{quote}
-%  
-%  New text:
-%  \begin{quote}
-%  In this first approach, we treat our system in terms of two well-known types of molecular
-%  motion which lead to anomalous subdiffusion: 
-%  \end{quote}
+    % BJC: This seems like the reviewer forcing his own style on us. And seems like a generalization
+    % based on only looking at figure 8. I could just modify parts of figure 8 to please him. But I
+    % think the rest are fine. What do you think?
 

### 2020-08-02 Ben_Manuscripts/hdphmm/Draft.tex
Near-complete draft of reviewer responses

@@
   constants because MSDs are often non-linear on the timescales accessible to molecular
-  simulation. Additionally, direct calculations of diffusion constant may obscure the
+  simulation. Additionally, direct calculations of diffusion constants may obscure the
   molecular mechanisms controlling transport, hindering the ability to understand or 
@@
   atomistic molecular model of four pores in a monoclinic unit cell with 
-  10\% water by weight. Approximately one third of the water molecules 
-  occupy the tail region with the rest are near the pore center.~\cite{coscia_chemically_2019}
+  10\% water by weight, totaling 62,000 atoms. Approximately one third of 
+  the water molecules occupy the tail region with the rest are near the pore 
+  center.~\cite{coscia_chemically_2019}
 
@@
   %BJC: added based on Chris' suggestion.
-  For the purposes of our analysis, we assume ergodicity of the 24 solute trajectories.
-  That is, we assume our MD simulations sample all possible states with the correct 
+  For the purposes of our analysis,
+  % we assume ergodicity of the 24 solute trajectories.
+  %That is, 
+  we assume our MD simulations sample all possible states with the correct 
   frequency.
@@
   method of trajectory generation. The following procedures correspond to the methods
-  described at the beginning of this section:
+  described above:
   \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]

### 2020-08-02 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
draft of response done. Updates to citations

@@
 \externaldocument[S-]{Supporting_Information}
-\externaldocument[M-]{Final_Draft}
+\externaldocument[M-]{Draft}
 
@@
     Author reply: We thank the reviewer for bringing our attention to these other interesting 
-    approaches. They certainly merit discussion as alternative approaches for measuring diffusivity
-    and selectivity. We have added some discussion of these methods to the introduction.
+    approaches. They certainly merit discussion as alternative approaches for estimating mean 
+    squared displacements on long timescales. We have added some discussion of these methods to 
+    the introduction.
 
     \begin{quote}
-    TBD
+    A number of approaches have been explored to inexpensively extend the relatively short
+    trajectories output by molecular simulations which exhibit complex diffusive behaviors
+    onto much longer timescales. The trajectory extending kinetic Monte Carlo (TEKMC) approach
+    divides a unit cell into a three dimensional grid and quantifies the transition 
+    probabilities of particles that can move between each subdivision allowing one to generate
+    stochastic trajectories that reach the diffusive regime~\cite{neyertz_trajectory-extending_2010}
+    It is possible to parameterize TEKMC models with relatively short simulation trajectories 
+    which facilitates systematic studies of small perturbations to material constituents.~\cite{hanson_computer_2012}
+    In a related approach, dynamic bond percolation (DBP) theory can be used to quantify the
+    rate of transition between sites in a dynamically disordered medium and long timescale
+    behavior can be propagated using kinetic Monte Carlo simulations.~\cite{druger_dynamic_1983}
+    Webb et al. extended this approach by defining sites based on the molecular details of 
+    a polymer electrolyte system, thus allowing them to explain ion diffusivities predicted by
+    the model in terms of chemically specific interactions.~\cite{webb_chemically_2015}
+    \end{quote}
+
+    We have also modified the first sentence of the paragraph that follows in order to maintain
+    good flow.
+
+    Original text:
+    \begin{quote}
+    We have already advanced our understanding of LLC monomer design in our previous work
+    by building stochastic time series models based on the chemical intuition gained
+    from qualitative MD studies of solute transport in an H\textsubscript{II} phase LLC
+    membrane.
+    \end{quote}
+
+    Modified text:
+    \begin{quote}
+    Based on the chemical intuition gained from our previous qualitative MD studies of 
+    solute transport in an H\textsubscript{II} phase LLC membrane, we have contributed our
+    own stochastic modeling approaches with goals similar to both TEKMC and DBP.
     \end{quote}
@@
     suited as a separate study where we could include a number of approaches, including perhaps
-    recent approaches we have developed within our research group.~\cite{} We would also prefer to have
+    recent approaches we have developed within our research group.~\cite{coscia_capturing_2020} We would also prefer to have
     sufficient time to appropriately implement the technique for our system. Although it seems a
@@
     approach to obtaining our first goal, but it is not clear that it could give the same level
-    of mechanistic insight that the HDP-AR-HMM offers. Although the work by Hansen et al.
+    of mechanistic insight that the HDP-AR-HMM offers. Although the work by Hanson et al.
     (J. Phys Chem. B, 2012, 116, 95-103) is able to provide physical insight into the effect of
@@
     order to hypothesize transport mechanisms. In this work we "re-discover" these mechanisms
-    and characterize them in detail using the HDP-AR-HMM while simultaneously providing a method 
-    to estimate diffusion constants.
+    with minimal human intervention and characterize them in detail using the HDP-AR-HMM while 
+    \textit{simultaneously} providing a method to estimate diffusion constants.
 
@@
     understanding that the scope of JPC has been expanded to welcome papers which focus on 
-    methodology. We have studied the structure of and transport within this particular LLC system
-    extensively in our previous work.\cite{} We feel strongly that our current work should 
+    methodology. We have studied the structure of and transport of solutes within this 
+    particular LLC system extensively in our previous work.\cite{coscia_chemically_2019} We feel strongly that our current work should 
     emphasize the HDP-AR-HMM as a more general tool for understanding complex dynamics in 
@@
     \begin{quote}
-      We studied transport of solutes in the H\textsubscript{II} phase using an atomistic 
-      molecular model of four pores in a monoclinic unit cell with 10\% water by weight, 
+      We studied transport of solutes in the H\textsubscript{II} phase using \hl{our
+      previously developed} atomistic molecular model of four pores in a 
+      \hl{$9.4\times9.4\times7.6$ nm} monoclinic unit cell with 10\% water by weight, 
       \hl{totaling 62,000 atoms}.    
@@
     \begin{quote}
-    %BJC: this is verbatim from last response to reviewers.
+    %BJC: this is verbatim from last response to reviewers so far
     We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
@@
     approaches so that a range of solutes and monomers could be self-consistently and easily 
-    studied. The main goal of this work is to develop stochastic models which can reproduce
+    studied. 
+    %BJC: The following wasn't explicitly asked for, so I could omit    
+    The main goal of this work is to develop stochastic models which can reproduce
     solute behavior on MD time scales, independent of the choice of force field. In future 
@@
     to very low water content LLC regimes (such as the 10\% LLC studied). For higher water content 
-    LLCs (e.g. > 15-20\%) it is straightforward to obtain the diffusion limit from standard MD 
+    LLCs (e.g. $>$ 15-20\%) it is straightforward to obtain the diffusion limit from standard MD 
     simulations. While the authors are surely well aware of this, the reader may not be, and it is
@@
     dynamical behavior even on short time scales can still be highly informative. This is the
-    basis for the point we make in the introduction: "...direct calculations of diffusion 
+    basis for the point we make in the introduction:``...direct calculations of diffusion 
     constants may obscure the molecular mechanisms controlling transport". Therefore we would
     prefer not to limit the range of application of this method. 
-    %BJC: could add something to the effect. If you only care about diffusivity, then this level of modeling isn't necessary in many systems.
+    %BJC: If it would be better to modify the text, then we could add something to the effect: If you only care about diffusivity, then this level of
+    % modeling isn't necessary in many systems.
 
@@
 
+    %BJC: figured I'd get your feedback on above before writing the part that will go into the text.
+
     %r1_comment6
@@
     caused by our use of the word 'ergodic'. Figure 7 clearly demonstrates that individual trajectories
-    are not by themselves ergodic. Our intention was to communicate our assumption that all 24 
+    are not by themselves ergodic. Our intention was to communicate our assumption that collectively all 24 
     trajectories visit all possible dynamic states with representative probability. This is 
-    necessary in order to make accurate long timescale predictions. The 5 $\mu_s$ length of our 
+    necessary in order to make accurate long timescale predictions. The 5 $\mu s$ length of our 
     simulations was intended to increase the validity of this assumption.
 
-    The use of the word 'ergodic' is not necessary, therefore we have modified the text as follow
-    to remove the source of miscommunication:
+    The use of the word `ergodic' is not necessary, therefore we have modified the text as follows
+    to remove the source of potential miscommunication:
 
@@
     dynamical data on shorter timescales. Using what we have learned about the radial distribution
-    functions of these solutes in this and our previous work\cite{}, it may be possible to 
+    functions of these solutes in this and our previous work~\cite{coscia_chemically_2019}, it may be possible to 
     learn how to create initial configurations with solutes initially distributed in a way that
     is close to their equilibrium distribution, allowing solutes to thoroughly explore the 
-    accessible membrane structural space more quickly and reducing the amount unequilibrated
+    accessible membrane structural space more quickly and reducing the amount of unequilibrated
     data that must be discarded. % could mention GCMC?
@@
     Author reply: We thank the reviewer for pointing out our potential errors. For the hydrogen bond
-    criteria we have updated the text from "D-H-A" to "H-D-A". Regarding page 15 line 8 (\textit{"Method 2:
-    Since trajectories generated by Method 2..."}), changing "Method 2" to "Method 1" would actually be 
+    criteria we have updated the text from ``D-H-A" to ``H-D-A". Regarding page 15 line 8 (``Method 2:
+    Since trajectories generated by Method 2..."), changing ``Method 2" to ``Method 1" would actually be 
     incorrect. At the beginning of Section 2.4, we defined two techniques for generating stochastic 
-    trajectories. 'Method 2' on page 15 line 8 describes the bootstrapping procedures for Method 2 of
+    trajectories. ``Method 2'' on page 15 line 8 describes the bootstrapping procedures for Method 2 of
     trajectory generation. This is a clear lack of clarity on the author's part and therefore we 
-    have made an effort to avoid to change our wording to avoid confusion.
+    have made an effort to modify our wording to avoid confusion.
 
@@
 \bibliographystyle{ieeetr}
-\bibliography{stochastic_transport}
+\bibliography{hdphmm}
 

### 2020-08-08 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
Small edits
Started response to reviewers for hdphmm
Tweaks for final manuscript.

@@
   dynamical behavior of different solutes based solely on the time series of 
-  their center of mass positions. The process of choosing the correct anomlous
+  their center of mass positions. The process of choosing the correct anomalous
   diffusion modeling approach provides its own mechanistic insight since it 
@@
   Despite relatively good predictions of the MD MSD, qualitative mismatch
-  between stoachastic and MD simulated trajectories suggest that the Markov
+  between stochastic and MD simulated trajectories suggest that the Markov
   state-dependent dynamical model may be giving the right answers for the
@@
   to form a clear connection between complex solute dynamics on the nanosecond 
-  timescale and macroscopic observables. On the nanoscopic scale, one can both 
+  timescale and macroscopic observables. On the nanoscale, one can both 
   learn and characterize dynamical modes in order to identify areas of potentially
@@
 % LocalWords:  bothmode todo eyetest Methanol's acid's subplots methanol's alt
-% LocalWords:  timestep pre selectivtiy foulants subfigures RWFs roman github
-% LocalWords:  al linkable nanopores klages
+% LocalWords:  time step pre selectivtiy foulants subfigures RWFs roman github
+% LocalWords:  al linkable nanopores klages BJCR BJCB MRSB BJCA BJCC
+% LocalWords:  Donnan steric Antechamber polarizable intramolecular
+% LocalWords:  quasiharmonic ester decorrelated nanoscale
+% LocalWords:  nanoscopic impactful

### 2020-08-08 Ben_Manuscripts/hdphmm/Draft.tex

@@
   chemically-specific manner. It would be extremely useful to experimentalists if we 
-  could connect LLC monomer design with measurable quantities. This goal is complicated
-  by the non-Brownian hopping and trapping behavior induced by the membrane's diverse
-  topology and inhomogeneous structure resulting in subdiffusive behavior out to 
-  multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
-
-  We have already advanced our understanding of LLC monomer design in our previous work
-  by building stochastic time series models based on the chemical intuition gained
-  from qualitative MD studies of solute transport in an H\textsubscript{II} phase LLC
-  membrane.~\cite{coscia_chemically_2019,coscia_capturing_2020} We identified three 
-  classes of trapping behavior which result in subdiffusion out to the microsecond 
+  could connect LLC monomer design with measurable quantities such as diffusivity and
+  selectivity. This goal is complicated by the non-Brownian hopping and trapping behavior
+  induced by the membrane's diverse topology and inhomogeneous structure resulting in 
+  subdiffusive behavior out to multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
+
+  %r1_comment2
+  A number of approaches have been explored to inexpensively extend the relatively short
+  trajectories output by molecular simulations which exhibit complex diffusive behaviors
+  onto much longer timescales. The trajectory extending kinetic Monte Carlo (TEKMC) approach
+  divides a unit cell into a three dimensional grid and quantifies the transition 
+  probabilities of particles that can move between each subdivision allowing one to generate
+  stochastic trajectories that reach the diffusive regime~\cite{neyertz_trajectory-extending_2010}
+  It is possible to parameterize TEKMC models with relatively short simulation trajectories 
+  which facilitates systematic studies of small perturbations to material constituents.~\cite{hanson_computer_2012}
+  In a related approach, dynamic bond percolation (DBP) theory can be used to quantify the
+  rate of transition between sites in a dynamically disordered medium and long timescale
+  behavior can be propagated using kinetic Monte Carlo simulations.~\cite{druger_dynamic_1983}
+  Webb et al. extended this approach by defining sites based on the molecular details of 
+  a polymer electrolyte system, thus allowing them to explain ion diffusivities predicted by
+  the model in terms of chemically specific interactions.~\cite{webb_chemically_2015}
+
+%  We have already advanced our understanding of LLC monomer design in our previous work
+%  by building stochastic time series models based on the chemical intuition gained
+%  from qualitative MD studies of solute transport in an H\textsubscript{II} phase LLC
+%  membrane.~\cite{coscia_chemically_2019,coscia_capturing_2020} 
+  Based on the chemical intuition gained from our previous qualitative MD studies of 
+  solute transport in an H\textsubscript{II} phase LLC membrane, we have contributed our
+  own stochastic modeling approaches with goals similar to both TEKMC and DBP.~\cite{coscia_chemically_2019,coscia_capturing_2020}
+  We identified three classes of trapping behavior which result in subdiffusion out to the microsecond 
   time scale. In our first approach to stochastically model this behavior, we treated 
@@
 
-  Although powerful and insightful, our previous work required considerable human effort
-  in order to analyze the MD trajectories and to hypothesize stochastic models which
-  matched the behavior of solutes. It would be significantly more useful and broadly 
+  Although powerful and insightful, TEKMC, DBP and our previous work required considerable
+  human effort in order to analyze the MD trajectories and to hypothesize stochastic models 
+  which matched the behavior of solutes. It would be significantly more useful and broadly 
   applicable if we could design an approach which distinguishes and parameterizes varied
@@
 
-  We studied transport of solutes in the H\textsubscript{II} phase using an
-  atomistic molecular model of four pores in a monoclinic unit cell with 
-  10\% water by weight, totaling 62,000 atoms. Approximately one third of 
-  the water molecules occupy the tail region with the rest are near the pore 
-  center.~\cite{coscia_chemically_2019}
+  We studied transport of solutes in the H\textsubscript{II} phase using our
+  previously developed atomistic molecular model of four pores in a $9.4\times9.4\times7.6$ nm 
+  monoclinic unit cell with 10\% water by weight, totaling 62,000 atoms. Approximately
+  one third of the water molecules occupy the tail region with the rest are near the
+  pore center.~\cite{coscia_chemically_2019}
+
+  %r1_comment3  
+  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
+  We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
+  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
+  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
+  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
+  and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
+  water model. We chose these standard force fields and generalizable parameterization 
+  approaches so that a range of solutes and monomers could be self-consistently and easily 
+  studied. The main goal of this work is to develop stochastic models which can reproduce
+  solute behavior on MD time scales, independent of the choice of force field. In future 
+  work, it may be beneficial to employ specialized force fields, including polarizable 
+  force fields or other higher-order effects in order to improve the accuracy of structure 
+  parameters and selectivity predictions.
 

### 2020-08-08 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
comments on response to reviewers.

@@
     %BJC: well Venkat Ganesan just relinquished his anonymity
+    %MRS: the paper will get in, I'm sure, and now we know better how he thinks, so all good.
     add a comprehensive discussion of how their approach compares to this and similar methods. The 
@@
 
+    %MRS: tweaked below.
     We agree that a full comparison of our method to other methods for computing long timescale 
@@
     suited as a separate study where we could include a number of approaches, including perhaps
-    recent approaches we have developed within our research group.~\cite{coscia_capturing_2020} We would also prefer to have
-    sufficient time to appropriately implement the technique for our system. Although it seems a
+    recent approaches we have developed within our research group.~\cite{coscia_capturing_2020}
+    Such a large-scale comparison would take more space and time than would be appropriate for the current paper.
+    % We would also prefer to have
+    %sufficient time to appropriately implement the technique for our system.
+    Although method such as TEKMC seems a
     fairly straightforward approach to implement, it is not immediately clear how we could
@@
     in response to different temperatures and nanoparticle concentrations. This is actually pretty
-    in line with the type of analysis we performed in our initial LLC work where we used the
-    mean squared displacement and the qualitative characteristic of the solute time series in
+    in line with the type of analysis we performed in our initial LLC work
+    %MRS: you mean your 2nd paper? refer specifically
+    where we used the mean squared displacement and the qualitative characteristic of the solute time series in
     order to hypothesize transport mechanisms. In this work we "re-discover" these mechanisms
@@
     %BJC: not sure if I should ignore the JCTC part completely or basically just say what the editor said.
+    %MRS: my response below (Basically, saying what the editor said, in case it is send back out).
     \item \textit{Much of the writing seems more suitable for JCTC rather than JPC. I encourage the
@@
 
-    Author reply: We thank the reviewer for encouraging us to include more physical insight and
-    further details about our molecular simulations. Regarding physical insight, it is our 
-    understanding that the scope of JPC has been expanded to welcome papers which focus on 
-    methodology. We have studied the structure of and transport of solutes within this 
-    particular LLC system extensively in our previous work.\cite{coscia_chemically_2019} We feel strongly that our current work should 
+    Author reply: We thank the reviewer for encouraging us to include
+    more physical insight and further details about our molecular
+    simulations. We received feedback from the editor along with these
+    comments that the scope of JPC has been expanding, and that the
+    methodological details are appropriate.
+    We have studied the structure of and transport of solutes within this 
+    particular LLC system extensively in our previous work.\cite{coscia_chemically_2019}
+    We feel strongly that our current work should 
     emphasize the HDP-AR-HMM as a more general tool for understanding complex dynamics in 
     systems beyond our example system. We would prefer not to cut any methodological details, as
-    this would hurt the paper's reproducibilty, and lengthening the paper by including additional
+    this would hurt the paper's reproducibility, and lengthening the paper by including additional
     physical insight may narrow the audience willing to dive in.
@@
     % paper? I would probably use the same pic anyways or something very similar.
+    %MRS: never bad to include pictures of the system, so go ahead.
 
@@
     solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
-    assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
+    assigned charges using the AM1-BCC model
+    %MRS: added (here, not in text)
+    as implemented in Antechamber.~\cite{jakalian_fast_2000,jakalian_fast_2002}
     GAFF is very commonly used in simulations with diverse organic chemical functionality, 
@@
     %BJC: The following wasn't explicitly asked for, so I could omit
+    %MRS: I think it's appropriate to include.
     The main goal of this work is to develop stochastic models which can reproduce
@@
     the time scales necessary to reach a diffusive regime will be much more attainable with 
-    standard MD. However, we do contend that our method would still be very useful for studying
-    solute dynamics in these higher water content systems. Interactions characterized by different
+    standard MD.
+    %MRS2: is this always the case?
+I think a more appropriate response would be "in systems with relatively unimpeded cores, such as in many cases LLCs with a higher water content, most waters will be relatively unimpeded, and diffusion constants can be obtained by standard techniques.
+    However, we do contend that our method would still be very useful for studying
+    solute dynamics in these higher water content systems.
+    %MRS: maybe "including the dynamics of solutes that have longer residence times and interact with portions of the system away from the pore center."
+    Interactions characterized by different
     dynamical behavior even on short time scales can still be highly informative. This is the
@@
     % modeling isn't necessary in many systems.
-
+    %MRS: I think good to talk about.
     %r1_comment5
@@
     % extensively about solute behavior in the tails so his steric argument is confusing me.
+
+    %MRS: It is a little confusing. First, we never use the term "pore
+    %radius", since the structure of the pore makes it very hard to
+    %define a single pore radius.  The term "pore region" is used once
+    %(about line 995), that that should probably be "pore center".
+    %Second, it's not clear what is meant when they say it's not clear
+    %how they are constrained when they must be by steric
+    %interactions.  Since steric interactions do NOT keep them in the
+    %pore region (at least for the smallest solutes).  Figure 2 is a selection of a trajectory.
+
     %    First, we would like to clarify
@@
 %    between pores (although we have not observed any).
-    The constraint on our stochastic simulations is built into the trajectory generation procedure.
+
+    %MRS: how about this?  We are grateful for the opportunity to
+    clarify some of the details of the simulation geometries.  We
+    avoid defining a ``pore radius'' in most cases, since many solutes
+    can easily partition partially into the pores, and the radial
+    distribution of head groups and even tail groups is changes over
+    several angstroms.~\cite{yourpapers} This partitioning occurs to the extent that smaller molecules like water and methanol can in fact
+    move between pores in rare instances.~\cite{yourpapers} However the rarity of the events and the fact that they occur parallel to transport means that they do not really affect transport, and can be interpreted mathematically as simply going deep into the wall and coming back again into the same pore.
+
+    Because of this, our stochastic simulations are constrained to remain close to a single pore by the trajectory generation procedure.
     Each state is parameterized by a mean in the radial direction computed based on the solute's 
     distance from the \textit{nearest pore center}, making it impossible for the solute to get 
-    further than the pore radius away. Each time a state change occurs, the mean position of the
+    further than
+    %MRS: maybe this instead?
+    %the pore radius.
+    half the pore-to-pore distance away.
+    %MRS: though I'm not QUITE sure that's right, since the hexagonal packing means that the transition between pores
+    %occurs at different distances depending on the angle. 
+    Each time a state change occurs, the mean position of the
     solute in the $r$ dimension jumps to the appropriate mean. However, in the axial direction, 
@@
     favor moves towards states that exist closer to the pore interiors. Alternatively, it may prove
-    necessary to constrain solute positions to the means in each dimension. However, this would require 
-    much more data and would likely require us to explore less expensive models as described in
-    the response to Reviewer 2 below.
+    necessary to constrain solute positions to the means in each dimension. However, these extension
+    are beyond the scope of the current paper.
+    %MRS: below not really needed.
+    %would require 
+    %much more data and would likely require us to explore less expensive models as described in
+    %the response to Reviewer 2 below.
 
@@
 
+    %MRS: So, I think they have a partial point, in that the caption
+    %should describe the figure, and the conclusions proved by the
+    %figure, not the process used to get to the figure so much.
+So maybe figure 8 should be "hydrogen bonds donated to the methanol to the highlighted oxygen atoms in three regions of the monomer are are shown: the carboxylate .
+.
+For each type of hydrogen bond in each predominant state, we show the 95th percentile of hydrogen bond lifetimes."  Does that make sense?
+
 \end{enumerate}
@@
     in this work as a benchmark to explore much less expensive models.
-    %BJC: I'm not exactly sure where to put this. Originally I thought conclusions because it's
-    %not really a method, but seemed to make the most sense near the system description.
+    %MRS: maybe focus more on understanding mechanisms, rather than screening?  So the length is not SO impractical.
     We propose some ideas to this end in the text we have added to the end of Section 2.1, where
@@
     of our system and length of the accompanying molecular simulations appears to be somewhat 
-    impractical. We would like to emphasize that our large, fully atomistic models will be
+    impractical.
+    We would like to emphasize that our large, fully atomistic models will be
     extremely valuable as a benchmark systems used to explore less expensive models. For example, we 
@@
     data that must be discarded. % could mention GCMC?
+    %MRS: sure.
     Finally, it may be possible to speed up our simulations by 
@@
     %, or by using hydrogen mass repartitioning to allow us to increase the MD time step. 
-
+    %MRS: zero on hydrogen bonding strength, which is thermodynamics.  It may affect H-bonding kinetics by
+    % increasing the timescales of tumbling (larger rotational inertia, slower rotational diffusion).  If molecules aren't free to tumble anyway, though,
+    % then the kinetics may be affected less. 
     \end{quote}
@@
 
-    We have also modified the text on page 15 line 8 from the orginal text:
+    We have also modified the text on page 15 line 8 from the original text:
     \begin{quote}
@@
 % LocalWords:  parametrization MSDs MSD timescales renormalizing MFPT
-% LocalWords:  bicontinuous Donnan steric em dt lyotropic
-% LocalWords:  subdiffusive
+% LocalWords:  bicontinuous Donnan steric em dt lyotropic Calderon al
+% LocalWords:  subdiffusive Nanostructured nanoporous TEKMC Phys Chem
+% LocalWords:  Venkat Ganesan DBP timescale Webb diffusivities HDP AR
+% LocalWords:  HMM nanoparticles penetrants nanoparticle JPC pic LLCs
+% LocalWords:  diffusivity gyroid solute's nanometer nanometers HPC
+% LocalWords:  carboxylate Dirichlet unequilibrated GCMC VMD docs

### 2020-08-09 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
some thoughts.
Incorporating MRS comments/suggestions

@@
     Macromolecules 2015, 48, 7346-7358, and J. Phys Chem. B, 2012, 116, 95-103. The authors should 
-    %BJC: well Venkat Ganesan just relinquished his anonymity
-    %MRS: the paper will get in, I'm sure, and now we know better how he thinks, so all good.
     add a comprehensive discussion of how their approach compares to this and similar methods. The 
@@
     recent approaches we have developed within our research group.~\cite{coscia_capturing_2020}
-    Such a large-scale comparison would take more space and time than would be appropriate for the current paper.
-    % We would also prefer to have
-    %sufficient time to appropriately implement the technique for our system.
-    Although method such as TEKMC seems a
-    fairly straightforward approach to implement, it is not immediately clear how we could
-    optimally adapt the methodology to a monoclinic unit cell with two dimensional order. 
+    Such a large-scale comparison would take more space and time than would be appropriate for 
+    the current paper. Although method such as TEKMC seems a fairly straightforward approach to
+    implement, it is not immediately clear how we could optimally adapt the methodology to a 
+    monoclinic unit cell with two dimensional order. 
 %    the grids that divide the homogeneous cubic unit cells of the referenced TEKMC studies to 
@@
     in response to different temperatures and nanoparticle concentrations. This is actually pretty
-    in line with the type of analysis we performed in our initial LLC work
-    %MRS: you mean your 2nd paper? refer specifically
-    where we used the mean squared displacement and the qualitative characteristic of the solute time series in
-    order to hypothesize transport mechanisms. In this work we "re-discover" these mechanisms
-    with minimal human intervention and characterize them in detail using the HDP-AR-HMM while 
-    \textit{simultaneously} providing a method to estimate diffusion constants.
+    in line with the type of analysis we performed in our initial LLC transport work (J. Phys Chem. B, 2019, 123, 6314-6330)
+    where we used the mean squared displacement and the qualitative characteristics of the solute
+    time series in order to hypothesize transport mechanisms. In this work we "re-discover" these
+    mechanisms with minimal human intervention and characterize them in detail using the 
+    HDP-AR-HMM while \textit{simultaneously} providing a method to estimate diffusion constants.
 
@@
 
-    Author reply: We thank the reviewer for encouraging us to include
-    more physical insight and further details about our molecular
-    simulations. We received feedback from the editor along with these
-    comments that the scope of JPC has been expanding, and that the
-    methodological details are appropriate.
-    We have studied the structure of and transport of solutes within this 
-    particular LLC system extensively in our previous work.\cite{coscia_chemically_2019}
-    We feel strongly that our current work should 
-    emphasize the HDP-AR-HMM as a more general tool for understanding complex dynamics in 
-    systems beyond our example system. We would prefer not to cut any methodological details, as
-    this would hurt the paper's reproducibility, and lengthening the paper by including additional
-    physical insight may narrow the audience willing to dive in.
+    Author reply: We thank the reviewer for encouraging us to include more physical insight and
+    further details about our molecular simulations. We received feedback from the editor along 
+    with these comments that the scope of JPC has been expanding, and that the methodological 
+    details are appropriate. We have studied the structure of and transport of solutes within 
+    this particular LLC system extensively in our previous work.~\cite{coscia_chemically_2019}
+    We feel strongly that our current work should emphasize the HDP-AR-HMM as a more general 
+    tool for understanding complex dynamics in systems beyond our example system. We would prefer
+    not to cut any methodological details, as this would hurt the paper's reproducibility, and
+    lengthening the paper by including additional physical insight may narrow the audience willing
+    to dive in.
 
+    %TODO    
     %BJC: probably could add a picture of the system. Or is it okay to just reference another
@@
 
-    We added the highlight text to the first sentence of the section:
+    We added the highlighted text to the first sentence of the section:
     \begin{quote}
@@
 
-    We have also added the following text describing the model: %BJC: not actually added yet
+    We have also added the following text describing the model:
     \begin{quote}
-    %BJC: this is verbatim from last response to reviewers so far
     We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
@@
     solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
-    assigned charges using the AM1-BCC model
-    %MRS: added (here, not in text)
-    as implemented in Antechamber.~\cite{jakalian_fast_2000,jakalian_fast_2002}
+    assigned charges using the AM1-BCC model as implemented in Antechamber.~\cite{jakalian_fast_2000,jakalian_fast_2002}
     GAFF is very commonly used in simulations with diverse organic chemical functionality, 
@@
     approaches so that a range of solutes and monomers could be self-consistently and easily 
-    studied. 
-    %BJC: The following wasn't explicitly asked for, so I could omit
-    %MRS: I think it's appropriate to include.
-    The main goal of this work is to develop stochastic models which can reproduce
+    studied. The main goal of this work is to develop stochastic models which can reproduce
     solute behavior on MD time scales, independent of the choice of force field. In future 
@@
 
-    Author reply: We thank the reviewer for making this point. In higher water content systems, 
-    the time scales necessary to reach a diffusive regime will be much more attainable with 
-    standard MD.
-    %MRS2: is this always the case?
-I think a more appropriate response would be "in systems with relatively unimpeded cores, such as in many cases LLCs with a higher water content, most waters will be relatively unimpeded, and diffusion constants can be obtained by standard techniques.
+    Author reply: We thank the reviewer for making this point. 
+    %BJC2: modded based on MRS suggestion    
+    In systems with less obstructions to motion, such as LLCs with a higher water content, most 
+    solutes and water will be relatively unimpeded, and diffusion constants can be obtained by 
+    standard techniques.    
     However, we do contend that our method would still be very useful for studying
-    solute dynamics in these higher water content systems.
-    %MRS: maybe "including the dynamics of solutes that have longer residence times and interact with portions of the system away from the pore center."
-    Interactions characterized by different
-    dynamical behavior even on short time scales can still be highly informative. This is the
-    basis for the point we make in the introduction:``...direct calculations of diffusion 
+    solute dynamics in these higher water content systems 
+    %BJC2: incorporated MRS suggestion with small modifications    
+    by allowing one to study the dynamics of solutes that have longer residence times and interact
+    with moieties in a complex medium. %portions of the system away from the pore center.
+    %Interactions characterized by different dynamical behavior even on short time scales can
+    %still be highly informative. 
+    This is the basis for the point we make in the introduction:``...direct calculations of diffusion 
     constants may obscure the molecular mechanisms controlling transport". Therefore we would
     prefer not to limit the range of application of this method. 
-    %BJC: If it would be better to modify the text, then we could add something to the effect: If you only care about diffusivity, then this level of
-    % modeling isn't necessary in many systems.
-    %MRS: I think good to talk about.
+    %BJC2: added    
+    However, we do agree that it would be helpful to the reader to clarify that the level of modeling 
+    which we present in this work is certainly not merited in cases where they are only interested in
+    diffusion constants. Therefore, we have modified a paragraph in the introduction in order to
+    encourage readers to pursue simpler approaches if the system allows it.
+
+    Updated text with additions highlighted in yellow:
+
+    In this work, we are particularly interested in the design of lyotropic liquid 
+    crystal (LLC) monomers, a class of amphiphilic molecules whose ordered self-assembled
+    phases can be cross-linked into mechanically strong membranes capable of highly 
+    selective separations. Inverted hexagonal phase, or H\textsubscript{II}, LLC membranes
+    are characterized by hexagonally packed, uniform-sized and straight pores, an ideal 
+    geometry for high throughput transport. Their pores are lined with the LLC monomer's
+    functional groups which can potentially be designed to interact with solutes in a 
+    chemically-specific manner. It would be extremely useful to experimentalists if we 
+    could connect LLC monomer design with measurable quantities such as diffusivity and
+    selectivity.\hl{In many systems, including LLC membranes with water contents higher
+    than the 10 wt\% water system studied here, making this connection can be relatively 
+    straightforward calculation with standard techniques since small solutes and water 
+    can move relatively unimpeded and therefore enter a diffusive regime on timescales 
+    accessible to MD. When possible, we encourage the reader to take advantage of the 
+    simplest approach possible. However, for the system that has capture our interest,} 
+    this goal is complicated by the non-Brownian hopping and trapping behavior induced 
+    by the membrane's diverse topology and inhomogeneous structure resulting in subdiffusive
+    behavior out to multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
+
     %r1_comment5
@@
     %(about line 995), that that should probably be "pore center".
+    %BJC2: changed pore region to pore center
     %Second, it's not clear what is meant when they say it's not clear
@@
 
-    %MRS: how about this?  We are grateful for the opportunity to
-    clarify some of the details of the simulation geometries.  We
-    avoid defining a ``pore radius'' in most cases, since many solutes
-    can easily partition partially into the pores, and the radial
-    distribution of head groups and even tail groups is changes over
-    several angstroms.~\cite{yourpapers} This partitioning occurs to the extent that smaller molecules like water and methanol can in fact
-    move between pores in rare instances.~\cite{yourpapers} However the rarity of the events and the fact that they occur parallel to transport means that they do not really affect transport, and can be interpreted mathematically as simply going deep into the wall and coming back again into the same pore.
+    %MRS: how about this?  
+    %BJC2: seems good. made some minor edits
+    We are grateful for the opportunity to clarify some of the details of the simulation 
+    geometries. We avoid defining a ``pore radius'' because the radial distribution of 
+    head groups and even tail groups is spread over several nanometers and we have
+    observed clear evidence that solutes can similarly partition radially throughout 
+    the pores.~\cite{coscia_understanding_2019,coscia_chemically_2019} 
+%    This partitioning occurs to the extent that smaller molecules like water and methanol
+%    can in fact move between pores in rare instances.
+    %BJC2: I don't think I've actually published anything stating or proving the above. 
+    %I think it's particularly hard to get by the crosslinks. But I do believe it could happen.
+    %rephrased with that in mind.
+    Therefore, it may be possible that, in rare instances, smaller molecules like water and
+    methanol may move between pores. However the rarity of these events and the fact that 
+    they occur orthogonal to the transport dimension means that they do not significantly 
+    affect transport, and can be interpreted mathematically as simply going deep into the 
+    dense tail region before returning to the same pore.
 
-    Because of this, our stochastic simulations are constrained to remain close to a single pore by the trajectory generation procedure.
-    Each state is parameterized by a mean in the radial direction computed based on the solute's 
-    distance from the \textit{nearest pore center}, making it impossible for the solute to get 
-    further than
-    %MRS: maybe this instead?
-    %the pore radius.
-    half the pore-to-pore distance away.
+    Because of this, our stochastic simulations are constrained to remain close to a single 
+    pore by the trajectory generation procedure. Each state is parameterized by a mean in 
+    the radial direction computed based on the solute's distance from the \textit{nearest 
+    pore center}, making it impossible for the solute to get further than approximately half
+    the pore-to-pore distance away (the exact maximum distance is an an angle-dependent 
+    quantity due to the hexagonally packed pore configuration).
     %MRS: though I'm not QUITE sure that's right, since the hexagonal packing means that the transition between pores
     %occurs at different distances depending on the angle. 
-    Each time a state change occurs, the mean position of the
-    solute in the $r$ dimension jumps to the appropriate mean. However, in the axial direction, 
-    we do not parameterize the mean since it should be unbounded in that dimension. The $z$ mean
-    of each segment is set based on the position immediately before the state change occurred.
+    %BJC: Yeah, I know what you mean. I added the bit in parentheses above to acknowledge that.
+    Each time a state change occurs, the mean position of the solute in the $r$ dimension 
+    jumps to the appropriate mean. However, in the axial direction, we do not parameterize 
+    the mean since it should be unbounded in that dimension. The $z$ mean of each segment 
+    is set based on the position immediately before the state change occurred.
 
@@
     in three dimensions and set the mean vector, $\mathbf{c}$ equal to $\mathbf{0}$. Of course, this
-    may result in solutes exploring a three dimensional shape that does not share the geometric 
+    may result in solutes exploring a three dimensional space that does not share the geometric 
     features of the studied phase. Our hypothesis is that we can add one or more additional 
@@
     favor moves towards states that exist closer to the pore interiors. Alternatively, it may prove
-    necessary to constrain solute positions to the means in each dimension. However, these extension
+    necessary to constrain solute positions to the means in each dimension. However, these extensions
     are beyond the scope of the current paper.
-    %MRS: below not really needed.
-    %would require 
-    %much more data and would likely require us to explore less expensive models as described in
-    %the response to Reviewer 2 below.
 

### 2020-08-09 Ben_Manuscripts/hdphmm/Draft.tex
Incorporating MRS comments/suggestions

@@
   selective separations. Inverted hexagonal phase, or H\textsubscript{II}, LLC membranes
-  are characterized by hexagonally packed, uniform-sized and straight pores, an ideal
-  geometry for high throughput transport. Their pores are lined with the LLC monomer's
-  functional groups which can potentially be designed to interact with solutes in a 
-  chemically-specific manner. It would be extremely useful to experimentalists if we 
-  could connect LLC monomer design with measurable quantities such as diffusivity and
-  selectivity. This goal is complicated by the non-Brownian hopping and trapping behavior
-  induced by the membrane's diverse topology and inhomogeneous structure resulting in 
-  subdiffusive behavior out to multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
+  are synthesized with 10 \% water by weight and are characterized by hexagonally packed,
+  uniform-sized and straight pores, an ideal geometry for high throughput transport. 
+  Their pores are lined with the LLC monomer's functional groups which can potentially 
+  be designed to interact with solutes in a chemically-specific manner. It would be 
+  extremely useful to experimentalists if we could connect LLC monomer design with 
+  measurable quantities such as diffusivity and selectivity.
+  %r1_comment4
+  In many systems, including LLC membranes with higher water contents, making this 
+  connection is a relatively straightforward calculation since small solutes and water
+  can move relatively unimpeded and therefore enter a diffusive regime on timescales
+  accessible to MD. When possible, we encourage the reader to take advantage of the
+  simplest approach possible.
+  However, in the systems of interested to us,
+  this goal is complicated by the non-Brownian hopping and trapping behavior induced by the membrane's diverse
+  topology and inhomogeneous structure resulting in subdiffusive behavior out to 
+  multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
 
@@
   solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
-  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
+  assigned charges using the AM1-BCC model as implemented in Antechamber.~\cite{jakalian_fast_2000,jakalian_fast_2002}
   GAFF is very commonly used in simulations with diverse organic chemical functionality, 
@@
   Acetic acid, urea and ethylene glycol are slightly larger than methanol and contain 
-  multiple polar substituents which stabilize them closer to the pore region.
+  multiple polar substituents which stabilize them closer to the pore center.
   These three solutes also participate in significantly more sodium ion association. 

### 2020-08-10 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
Edits, new figure, new references

@@
 
+%MRS: additional thoughts:
+
+%1. Dynamic Bond Percolation theory (both the original version and the
+%chemically specific one) an and TEKMC are based on spatial clustering
+%and coarse-graining. Our approach is based on clustering and
+%coarse-graining the dynamics.  Can be more powerful, doesn't assume
+%(or minimally assumes - in some cases we assume pore vs. nono-pore)
+%which configurations are important, which matters when there are a
+%diversity of different types of bound states, and diversity of
+%dynamics (in the pore, associated with the head groups, etc).
+
+%2. Dynamical behavior is more complex with our solutes than ion
+%interactions because of the richer range of interactions involved
+%(ionic binding PLUS hydrophobic binding, i.e. more types of bound
+%states; it's not just binding and hopping, and thus something
+
+%3. Configurational behavior is more complex with the nanostructures,
+%because one cannot simply divide the structure into cubes
+%isotropically.  It may be easier to use our approach with more
+%diverse configurations, because we don't need to worry about
+%partitioning correctly.  This does push some of the difficulty into
+%choosing the coordinate system for the dynamics, but we have a lot
+%more freedom about choosing coordinate systems for the model than one
+%would using a uniform (or even nonuniform) partitioning of the
+%system. Yes, there are difficult choices to make but the model has
+%the freedom to make these choices.
+
+%4. One reason our simulations are longer because the timescales of
+%events observed generally are longer, and the number of solutes we
+%can put into the simulation is smaller (since the total pore volume
+%is smaller than it would be in an amorphous polymer).
+
+%5. We could probably construct our model it with a larger number of
+%more shorter simulations as well. Rare events require long timescale
+%sisulations.  However, the equilibration times for these simulations
+%(since we build from geometry, not from amorphous melts) are such
+%that we probably get more efficient use of simulations by running
+%fewer, longer simulations.
+
+%6. So it's not clear that this method is better than DBP or TEKMC
+% (especially since the results are a big ambiguous); one could define
+% bound states, and look at hops betwen then.  But it's definitely
+% DIFFERENT, it's not really the same thing at all, and we should push
+% back that it is similar.  We can argue that our approach is more
+% suited to our systems than the two configuration-based approaches -
+% one COULD try to use those approaches and they could be made to
+% work, but it's not a trivial thing to do, and we wanted to try
+% something where the data informed our model more completely and we
+% wouldn't have to try those modifications.
+
     %r1_comment3
@@
     to dive in.
-
-    %TODO    
-    %BJC: probably could add a picture of the system. Or is it okay to just reference another
-    % paper? I would probably use the same pic anyways or something very similar.
-    %MRS: never bad to include pictures of the system, so go ahead.
 
@@
     \end{quote}
+
+    Finally, we have added a figure with a picture of the system which we are studying:
+    \begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{membrane_side_profile.pdf}
+    \caption{When combined with 10 wt\% water, the LLC monomer studied in this work forms the 
+    H\textsubscript{II} phase which is characterized by hexagonally packed columns with 
+    hydrophilic pores. In the figure, white and red water molecules mark the membrane pores.
+    The monomer fills the rest of the space. Note that water molecules are present in the 
+    tails, but they are hidden for the sake of clarity. }\label{fig:membrane_side_profile}
+    \end{figure}
 
@@
     affect transport, and can be interpreted mathematically as simply going deep into the 
-    dense tail region before returning to the same pore.
+    tail region before returning to the same pore.
 
@@
 
+    We have strengthened Section 2.3 of the methods by adding a clearer discussion of the above.
+
+    Original text:
+    \begin{quote}
+    We obtained the mean vectors, $\mathbf{c}$, of the clustered states by averaging each 
+    value of the $\mathbf{c}$ vectors assigned to the same cluster. Note that we only care 
+    about the $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$ because solute trajectories are not 
+    bound in the $z$ direction.
+    \end{quote}
+
+    Modified text:
+
+    \begin{quote}
+    We obtained the mean vectors, $\mathbf{c}$, of the clustered states by averaging each 
+    value of the $\mathbf{c}$ vectors assigned to the same cluster. Note that we only care 
+    about the $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$. We do not parameterize the mean
+    $z$ position of particles because solute trajectories should not be bound to discrete
+    points in the axial direction. However, we do intentionally limit the radial location 
+    of particles in our stochastic trajectories to discrete values of $r$, effectively 
+    constraining them to stay within a single pore. While it's possible that, in rare cases,
+    solutes might move between adjacent pores, it would have no effect on axial transport
+    since this motion is orthogonal to the pore axis and because all pores are structurally
+    similar. This treatment assumes that a move between pores is equivalent to a solute 
+    which travels deep into the monomer tail region before returning to the same pore. 
+    \end{quote}
+
     The generalization of this procedure to three dimensions will be under active investigation 
@@
     are beyond the scope of the current paper.
+
+    We have added the following text to the end of Section 2.3 in order to make it clear that
+    the trajectory generation procedure will require more thought for different geometries:
+    \begin{quote}
+    The parameterization of $\mathbf{c}$, $A$ and $\Sigma$ as presented above has been designed 
+    specifically for the cylindrical pore geometry at hand. Our group is actively investigating
+    appropriate ways to parameterize more complicated geometries such as bicontinuous cubic phase
+    LLC membranes. 
+    \end{quote}
 
@@
     calculated...”, “We also analyzed...” should be omitted in figure captions.}
-    % BJC: This seems like the reviewer forcing his own style on us. And seems like a generalization
-    % based on only looking at figure 8. I could just modify parts of figure 8 to please him. But I
-    % think the rest are fine. What do you think?
 
-    %MRS: So, I think they have a partial point, in that the caption
-    %should describe the figure, and the conclusions proved by the
-    %figure, not the process used to get to the figure so much.
-So maybe figure 8 should be "hydrogen bonds donated to the methanol to the highlighted oxygen atoms in three regions of the monomer are are shown: the carboxylate .
-.
-For each type of hydrogen bond in each predominant state, we show the 95th percentile of hydrogen bond lifetimes."  Does that make sense?
+    %BJC2: okay, modified as suggested
+    Author reply: We agree with the reviewer that the type of wording described should not be
+    included in captions as their primary purpose should be to explain the conclusions drawn
+    by the figure rather the process of generating the figure. However, we believe that the 
+    only real offender among our captions was Figure 8. Therefore we have modified the language
+    of that figure:
+
+    Original caption:
+    \begin{quote}
+    (a) We analyzed hydrogen bonds donated by methanol to the highlighted oxygen
+    atoms in three regions of the monomer: the carboxylate groups (blue), the ether linkages
+    (green) and the tails (red). (b) For each predominant state (states 1--5 described in 
+    Figure~\ref{M-fig:prevalence}), we plotted the fraction of the total time in that state 
+    spent hydrogen bonding to various regions of the monomer, color coded to match (a).
+    (c) For each type of hydrogen bond in each predominant state, we calculated the 95th percentile
+    of hydrogen bond lifetimes. (d) We also analyzed the frequency and lifetimes of solute 
+    association with sodium ions. Methanol associates with sodium less than 10\% of the total 
+    time it occupies any of the predominant states.
+    \end{quote}
+
+    Modified caption:
+    \begin{quote}
+    (a) Hydrogen bonds can be donated by methanol to the highlighted oxygen atoms in three 
+    regions of the monomer: the carboxylate groups (blue), the ether linkages (green) and the
+    tails (red). (b) For each predominant state (states 1--5 described in Figure~\ref{M-fig:prevalence}),
+    we show the fraction of the total time in that state spent hydrogen bonding to various regions
+    of the monomer, color coded to match (a). (c) For each type of hydrogen bond in each predominant
+    state, we show the 95th percentile of hydrogen bond lifetimes. (d) We also show the 
+    frequency and lifetimes of solute association with sodium ions. Methanol associates with sodium
+    less than 10\% of the total time it occupies any of the predominant states.    
+    \end{quote}
 
@@
 
+    % BJC2: shifted initial focus towards mechnistic understanding. Still kept part about speeding up simulations
+    % as I think it's worth discussing ways to make this an actual high throughput technique. 
     Author reply: We thank the reviewer for pushing us to further evaluate the practicality of our
-    method as a tool for experimentalists. In short, there are many ways we can envision that 
-    would make this approach more amenable to high throughput simulations. The length of our 
-    simulations in this paper are indeed quite long. The dynamics of the solutes are somewhat 
-    slow and we wanted to ensure we gathered enough data for a sufficient parameterization. 
-    Putting aside brute force high throughput simulations that could be enabled by the 
-    ever-increasing availability of HPC resources, it would be to our benefit to use the system
-    in this work as a benchmark to explore much less expensive models.
-    %MRS: maybe focus more on understanding mechanisms, rather than screening?  So the length is not SO impractical.
-    We propose some ideas to this end in the text we have added to the end of Section 2.1, where
-    our simulations are described:
+    method as a tool for experimentalists. The length of our simulations in this paper are indeed 
+    quite long. 
+    %The dynamics of the solutes are somewhat slow and we wanted to ensure we gathered
+    %enough data for a sufficient parameterization. 
+    However, the length of the simulations primarily influences the reliability of the long
+    timescale predictions of our model. We believe one of our method's greatest strengths is its 
+    ability to elucidate transport mechanisms by automatically detecting shifts in dynamical
+    behavior, which can be achieved with much shorter simulations. 
+    In our previous work, we showed that one can use shorter simulations to uncover the same 
+    mechanisms which we described in our current work.~\cite{coscia_chemically_2019} However, the
+    HDP-AR-HMM makes it much simpler to identify these mechanisms. Our approach allows one to 
+    quickly identify behavior characteristic of solutes in terms of chemical functionality, 
+    allowing them to eliminate sets of potential LLC monomers on the basis of this more general
+    mechanistic understanding.
+
+    There is also value in considering ways to make high throughput simulation of this type of 
+    system attainable. Putting aside brute force high throughput simulations that could be enabled 
+    by the ever-increasing availability of HPC resources, it would be to our benefit to use the
+    system in this work as a benchmark to explore much less expensive models. We propose some ideas
+    to this end in the text we have added to the end of Section 2.1, where our simulations are described:
     \begin{quote}
@@
     of our system and length of the accompanying molecular simulations appears to be somewhat 
-    impractical.
-    We would like to emphasize that our large, fully atomistic models will be
-    extremely valuable as a benchmark systems used to explore less expensive models. For example, we 
-    could explore systems built with fewer LLC monomers by making the membrane pores shorter. We 
-    could also build systems with higher concentrations of solutes in order to gather more 
+    impractical. Dependent on one's goals, it may not be necessary to run such long simulations in order 
+    to extract valuable mechanistic insight. We originally uncovered the mechanisms discussed
+    in this study using trajectories a fraction of the length here.\cite{coscia_chemically_2019} A 
+    strong mechanistic understanding of solute transport with respect to the chemical features of a 
+    given LLC monomer may be enough for experimentalists to eliminate entire subsets of potential
+    design changes. However, it may still be valuable to consider how one might make these simulations
+    amenable to high-throughput studies. We would like to emphasize that our large, fully atomistic 
+    models will be extremely valuable as a benchmark system used to explore less expensive models. 
+    For example, we could explore systems built with fewer LLC monomers by making the membrane pores
+    shorter. We could also build systems with higher concentrations of solutes in order to gather more 
     dynamical data on shorter timescales. Using what we have learned about the radial distribution
@@
     accessible membrane structural space more quickly and reducing the amount of unequilibrated
-    data that must be discarded. % could mention GCMC?
-    %MRS: sure.
-    Finally, it may be possible to speed up our simulations by 
-    reducing the number of atoms using united-atom representations of the liquid crystal monomers.
-    %BJC: How strong of an influence would hydrogen mass repartitioning have on hydrogen bonding?
-    %, or by using hydrogen mass repartitioning to allow us to increase the MD time step. 
-    %MRS: zero on hydrogen bonding strength, which is thermodynamics.  It may affect H-bonding kinetics by
-    % increasing the timescales of tumbling (larger rotational inertia, slower rotational diffusion).  If molecules aren't free to tumble anyway, though,
-    % then the kinetics may be affected less. 
+    data that must be discarded. Alternatively, we could use grand canonical Monte Carlo simulations
+    to load solutes into the membrane~\cite{snurr_prediction_1993}. Finally, it may be possible 
+    to speed up our simulations by reducing the number of atoms using united-atom representations
+    of the liquid crystal monomers~\cite{horta_gromos-compatible_2016} or by using hydrogen mass 
+    repartitioning to allow us to increase the MD time step.~\cite{hopkins_long-time-step_2015}
     \end{quote}
@@
     %BJC: This is copied straight from the reviewer response for the previous paper.
+    %BJC2: do you think I should reword this at all to make it different?
     Author reply: The reviewer makes a valid point. This work started in parallel with experimental
@@
     \end{quote}
+
     to:

### 2020-08-10 Ben_Manuscripts/hdphmm/Draft.tex
Edits, new figure, new references

@@
 
-  %BJC: reworked this section for better clarity as it confused Chris
-  \textit{Obtaining Parameters of Clustered States}: We obtained the 
-  mean vectors, $\mathbf{c}$, of the clustered states by averaging each 
-  value of the $\mathbf{c}$ vectors assigned to the same cluster. Note 
-  that we only care about the $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$ 
-  because solute trajectories are not bound in the $z$ direction.
+  %BJC: r1_comment5
+  \textit{Obtaining Parameters of Clustered States}: We obtained the mean vectors,
+  $\mathbf{c}$, of the clustered states by averaging each value of the $\mathbf{c}$
+  vectors assigned to the same cluster. Note that we only care about the 
+  $r=\sqrt{x^2+y^2}$ portion of $\mathbf{c}$. We do not parameterize the mean
+  $z$ position of particles because solute trajectories should not be bound to discrete
+  points in the axial direction. However, we do intentionally limit the radial location 
+  of particles in our stochastic trajectories to discrete values of $r$, effectively 
+  constraining them to stay within a single pore. While it's possible that, in rare cases,
+  solutes might move between adjacent pores, it would have no effect on axial transport
+  since this motion is orthogonal to the pore axis and because all pores are structurally
+  similar. This treatment assumes that a move between pores is equivalent to a solute 
+  which travels deep into the monomer tail region before returning to the same pore.
 
@@
 
-%  In Section~\ref{S-section:ihmm_procedure} of the Supporting
-%  Information, we provide a step-by-step illustration of the following process.
+  %r1_comment5
+  The parameterization of $\mathbf{c}$, $A$ and $\Sigma$ as presented above has been designed 
+  specifically for the cylindrical pore geometry at hand. Our group is actively investigating
+  appropriate ways to parameterize more complicated geometries such as bicontinuous cubic phase
+  LLC membranes.
 

### 2020-08-10 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
Modifications and additions. Addressing requested non-scientific changes

@@
     stochastic trajectories that reach the diffusive regime~\cite{neyertz_trajectory-extending_2010}
-    It is possible to parameterize TEKMC models with relatively short simulation trajectories 
-    which facilitates systematic studies of small perturbations to material constituents.~\cite{hanson_computer_2012}
+    If the dynamics of the system are fast enough, it is possible to parameterize TEKMC models with
+    relatively short simulation trajectories which facilitates systematic studies of small perturbations
+    to material constituents.~\cite{hanson_computer_2012}
     In a related approach, dynamic bond percolation (DBP) theory can be used to quantify the
@@
 
-    %MRS: tweaked below.
+    %BJC2: 
     We agree that a full comparison of our method to other methods for computing long timescale 
     diffusion such as TEKMC would be very interesting and instructive but feel it would be better 
-    suited as a separate study where we could include a number of approaches, including perhaps
+    suited as a separate study where we could evaluate a number of approaches, including perhaps
     recent approaches we have developed within our research group.~\cite{coscia_capturing_2020}
+    %BJC2: added to make the point about our system being more complicated than those studied.
+    It would be illuminating to test these methods on systems such as ours where there is
+    a rich diversity of intermolecular interactions that work to immobilize solutes.
     Such a large-scale comparison would take more space and time than would be appropriate for 
-    the current paper. Although method such as TEKMC seems a fairly straightforward approach to
+    the current paper. Although methods such as TEKMC seems a fairly straightforward approach to
     implement, it is not immediately clear how we could optimally adapt the methodology to a 
-    monoclinic unit cell with two dimensional order. 
+    monoclinic unit cell with two dimensional order without in-depth testing.
     % the grids that divide the homogeneous cubic unit cells of the referenced TEKMC studies to 
     % our system which uses a monoclinic unit cell and has 2 dimensional order. 
+    %BJC2: maybe push back on the CS-DBP here? 
+    Regarding the CS-DBP model, we are not convinced it would be suitable for our goals because
+    it relies on defining bound states and modeling hops between them. There are numerous potential
+    locations within our LLC system where solutes can become bound in some way. The HDP-AR-HMM
+    circumvents the need for relatively complicated methods used to identify binding sites 
+    by automatically identifying distinct dynamics characteristic of a class of bound states.
 
@@
 
+%BJC2: I believe I had orginally addressed this briefly as well. Feel free to expand if you feel there is more to be said
 %3. Configurational behavior is more complex with the nanostructures,
@@
 
+% BJC2: assuming this comment about CS-DBP?
 %6. So it's not clear that this method is better than DBP or TEKMC
@@
 
-    Finally, we have added a figure with a picture of the system which we are studying:
+    Finally, we have added a figure with a picture of the system which we are studying 
+    (see~\ref{fig:membrane_side_profile}).
     \begin{figure}
@@
 
+    \begin{quote}
     In this work, we are particularly interested in the design of lyotropic liquid 
@@
     could connect LLC monomer design with measurable quantities such as diffusivity and
-    selectivity.\hl{In many systems, including LLC membranes with water contents higher
+    selectivity. \hl{In many systems, including LLC membranes with water contents higher
     than the 10 wt\% water system studied here, making this connection can be relatively 
@@
     accessible to MD. When possible, we encourage the reader to take advantage of the 
-    simplest approach possible. However, for the system that has capture our interest,} 
+    simplest approach possible. However, for the system that has captured our interest,} 
     this goal is complicated by the non-Brownian hopping and trapping behavior induced 
@@
     behavior out to multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
+    \end{quote}
 
@@
 
-    Author reply: We thank the reviewer for posing this question as this a constraint to which 
-    we gave thought but neglected to emphasize in the main text. 
+    Author reply: 
+    %We thank the reviewer for posing this question as this a constraint to which 
+    %we gave thought but neglected to emphasize in the main text. 
     %BJC: he's not saying that solutes should stay in the aqueous pore region right? We talk pretty
@@
     Author reply: We thank the reviewer for identifying the potential confusion that could be
-    caused by our use of the word 'ergodic'. Figure 7 clearly demonstrates that individual trajectories
+    caused by our use of the word `ergodic'. Figure 7 clearly demonstrates that individual trajectories
     are not by themselves ergodic. Our intention was to communicate our assumption that collectively all 24 

### 2020-08-10 Ben_Manuscripts/hdphmm/Draft.tex
Modifications and additions. Addressing requested non-scientific changes

@@
   are synthesized with 10 \% water by weight and are characterized by hexagonally packed,
-  uniform-sized and straight pores, an ideal geometry for high throughput transport. 
+  uniform-sized and straight pores, an ideal geometry for high throughput transport (see
+  Figure~\ref{fig:membrane_side_profile}). 
   Their pores are lined with the LLC monomer's functional groups which can potentially 
@@
   %r1_comment4
-  In many systems, including LLC membranes with higher water contents, making this 
-  connection is a relatively straightforward calculation since small solutes and water
-  can move relatively unimpeded and therefore enter a diffusive regime on timescales
-  accessible to MD. When possible, we encourage the reader to take advantage of the
-  simplest approach possible.
-  However, in the systems of interested to us,
-  this goal is complicated by the non-Brownian hopping and trapping behavior induced by the membrane's diverse
+  In many systems, including LLC membranes with water contents higher than the 10 wt\% 
+  water system studied here, making this connection can be relatively straightforward 
+  calculation with standard techniques since small solutes and water can move relatively
+  unimpeded and therefore enter a diffusive regime on timescales accessible to MD. When
+  possible, we encourage the reader to take advantage of the simplest approach possible. 
+  However, for the system that has captured our interest, this goal is complicated by 
+  the non-Brownian hopping and trapping behavior induced by the membrane's diverse
   topology and inhomogeneous structure resulting in subdiffusive behavior out to 
   multiple microseconds of simulation.~\cite{coscia_understanding_2019,coscia_chemically_2019}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{membrane_side_profile.pdf}
+  \caption{When combined with 10 wt\% water, the LLC monomer studied in this work forms the 
+    H\textsubscript{II} phase which is characterized by hexagonally packed columns with 
+    hydrophilic pores. In the figure, white and red water molecules mark the membrane pores.
+    The monomer fills the rest of the space. Note that water molecules are present in the 
+    tails, but they are hidden for the sake of clarity.}\label{fig:membrane_side_profile}
+  \end{figure}
 
@@
   thermostat~\cite{bussi_canonical_2007} respectively. We recorded configurations every 0.5 ns.
+
+  In consideration of our ultimate goal, which is to use high-throughput simulations to 
+  facilitate our understanding of LLC membrane design for solute-specific separations, the size 
+  of our system and length of the accompanying molecular simulations appears to be somewhat 
+  impractical. Dependent on one's goals, it may not be necessary to run such long simulations in order 
+  to extract valuable mechanistic insight. We originally uncovered the mechanisms discussed
+  in this study using trajectories a fraction of the length here.\cite{coscia_chemically_2019} A 
+  strong mechanistic understanding of solute transport with respect to the chemical features of a 
+  given LLC monomer may be enough for experimentalists to eliminate entire subsets of potential
+  design changes. However, it may still be valuable to consider how one might make these simulations
+  amenable to high-throughput studies. We would like to emphasize that our large, fully atomistic 
+  models will be extremely valuable as a benchmark system used to explore less expensive models. 
+  For example, we could explore systems built with fewer LLC monomers by making the membrane pores
+  shorter. We could also build systems with higher concentrations of solutes in order to gather more 
+  dynamical data on shorter timescales. Using what we have learned about the radial distribution
+  functions of these solutes in this and our previous work~\cite{coscia_chemically_2019}, it may be possible to 
+  learn how to create initial configurations with solutes initially distributed in a way that
+  is close to their equilibrium distribution, allowing solutes to thoroughly explore the 
+  accessible membrane structural space more quickly and reducing the amount of unequilibrated
+  data that must be discarded. Alternatively, we could use grand canonical Monte Carlo simulations
+  to load solutes into the membrane~\cite{snurr_prediction_1993}. Finally, it may be possible 
+  to speed up our simulations by reducing the number of atoms using united-atom representations
+  of the liquid crystal monomers~\cite{horta_gromos-compatible_2016} or by using hydrogen mass 
+  repartitioning to allow us to increase the MD time step.~\cite{hopkins_long-time-step_2015}
 
@@
 
-  \bibliographystyle{ieeetr}
+  % \bibliographystyle{ieeetr}
   \bibliography{hdphmm}

### 2020-08-11 Ben_Manuscripts/hdphmm/Draft.tex
Some additions to put things in context.

@@
 
-  Overall, this work provides a promising way to simultaneously identify transport 
+  This work provides a promising way to simultaneously identify transport 
   mechanisms in nanoporous materials and project complex diffusive behavior on
@@
   own stochastic modeling approaches with goals similar to both TEKMC and DBP.~\cite{coscia_chemically_2019,coscia_capturing_2020}
-  We identified three classes of trapping behavior which result in subdiffusion out to the microsecond 
+  In previous studies, we identified three classes of trapping behavior which result in subdiffusion out to the microsecond 
   time scale. In our first approach to stochastically model this behavior, we treated 
@@
 
-  In this work we attempt to uncover similar physical meaning through a data-driven process. 
-  We utilize the sticky hierarchical Dirichlet process autoregressive hidden Markov model 
-  (HDP-AR-HMM), a nonparameteric Bayesian classification technique that allows the user to 
-  automatically detect and infer the parameters of an unknown number of latent vector
-  autoregressive (VAR) modes present in solute center-of-mass MD 
-  trajectories.~\cite{fox_bayesian_2010} The sticky HDP-AR-HMM greatly extends the 
-  basic framework of simpler but more limited finite hidden Markov modeling approaches.
+  In this work we attempt to uncover similar physical meaning through
+  a data-driven process in which we characterize the local behavior of
+  the system through analysis of the dynamical characteristics o
+  particle trajectories.  This differs from other other approaches
+  such as TEKMC and DBP than cluster based on configurations visited
+  to extend the trajectories. We utilize the sticky hierarchical
+  Dirichlet process autoregressive hidden Markov model (HDP-AR-HMM), a
+  nonparameteric Bayesian classification technique that allows the
+  user to automatically detect and infer the parameters of an unknown
+  number of latent vector autoregressive (VAR) modes present in solute
+  center-of-mass MD trajectories.~\cite{fox_bayesian_2010} The sticky
+  HDP-AR-HMM greatly extends the basic framework of simpler but more
+  limited finite hidden Markov modeling approaches.
 
@@
 % LocalWords:  shirtsgroup superdiffusive diffusivities jazani wang persson CPC
-% LocalWords:  shortlag jupyter ester
+% LocalWords:  shortlag jupyter ester wt TEKMC DBP Webb Antechamber
+% LocalWords:  polarizable unequilibrated traj bicontinuous

### 2020-08-11 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
Soem comments.

@@
     by testing hypotheses motivated by observations of the diffusion constant (predicted by TEKMC)
-    in response to different temperatures and nanoparticle concentrations. This is actually pretty
-    in line with the type of analysis we performed in our initial LLC transport work (J. Phys Chem. B, 2019, 123, 6314-6330)
+    in response to different temperatures and nanoparticle concentrations. This parallels well
+    with the type of analysis we performed in our initial LLC transport work (J. Phys Chem. B, 2019, 123, 6314-6330)
     where we used the mean squared displacement and the qualitative characteristics of the solute
@@
 %coarse-graining the dynamics.  Can be more powerful, doesn't assume
-%(or minimally assumes - in some cases we assume pore vs. nono-pore)
+%(or minimally assumes - in some cases we assume pore vs. non-pore)
 %which configurations are important, which matters when there are a
@@
 % BJC2: assuming this comment about CS-DBP?
+    % MRS2: sorry, this was about OUR method, that it's definitely different because
+    % the clustering is not confiugurations based.
 %6. So it's not clear that this method is better than DBP or TEKMC
@@
     standard techniques.    
-    However, we do contend that our method would still be very useful for studying
+    However, we would still argue that our method would still be very useful for studying
     solute dynamics in these higher water content systems 
@@
     %still be highly informative. 
-    This is the basis for the point we make in the introduction:``...direct calculations of diffusion 
+    This is the basis for the point we make in the introduction:``. . . direct calculations of diffusion 
     constants may obscure the molecular mechanisms controlling transport". Therefore we would
@@
     tails (red). (b) For each predominant state (states 1--5 described in Figure~\ref{M-fig:prevalence}),
-    we show the fraction of the total time in that state spent hydrogen bonding to various regions
-    of the monomer, color coded to match (a). (c) For each type of hydrogen bond in each predominant
-    state, we show the 95th percentile of hydrogen bond lifetimes. (d) We also show the 
-    frequency and lifetimes of solute association with sodium ions. Methanol associates with sodium
+    the fraction of the total time in that state spent hydrogen bonding to various regions
+    of the monomer, color coded to match (a). (c) The 95th percentile of hydrogen bond lifetimes for
+    each type of hydrogen bond in each predominant state, the 95th percentile of hydrogen bond lifetimes
+    (d) The frequency and lifetimes of solute association with sodium ions. Methanol associates with sodium
     less than 10\% of the total time it occupies any of the predominant states.    
@@
 % LocalWords:  carboxylate Dirichlet unequilibrated GCMC VMD docs
+% LocalWords:  nono

### 2020-08-11 Ben_Manuscripts/hdphmm/Draft.tex
Soem comments.

@@
 
-  In consideration of our ultimate goal, which is to use high-throughput simulations to 
+  Given our ultimate goal, to use high-throughput simulations to 
   facilitate our understanding of LLC membrane design for solute-specific separations, the size 
-  of our system and length of the accompanying molecular simulations appears to be somewhat 
-  impractical. Dependent on one's goals, it may not be necessary to run such long simulations in order 
+  of our system and length of the accompanying molecular simulations appears may be somewhat 
+  impractical. In many situations, it may not be necessary to run such long simulations in order 
   to extract valuable mechanistic insight. We originally uncovered the mechanisms discussed
-  in this study using trajectories a fraction of the length here.\cite{coscia_chemically_2019} A 
+  in this study using trajectories a fraction of the length here~\cite{coscia_chemically_2019}. A 
   strong mechanistic understanding of solute transport with respect to the chemical features of a 
   given LLC monomer may be enough for experimentalists to eliminate entire subsets of potential
-  design changes. However, it may still be valuable to consider how one might make these simulations
-  amenable to high-throughput studies. We would like to emphasize that our large, fully atomistic 
+  design changes. However, it is still valuable to consider how one might make these simulations
+  amenable to high-throughput studies. We emphasize that our large, fully atomistic 
   models will be extremely valuable as a benchmark system used to explore less expensive models. 
@@
   data that must be discarded. Alternatively, we could use grand canonical Monte Carlo simulations
-  to load solutes into the membrane~\cite{snurr_prediction_1993}. Finally, it may be possible 
-  to speed up our simulations by reducing the number of atoms using united-atom representations
-  of the liquid crystal monomers~\cite{horta_gromos-compatible_2016} or by using hydrogen mass 
+  to load solutes into the membrane~\cite{snurr_prediction_1993}.
+  If simulation resources are available, the simulations could be split up into larger numbers of shorter simulations.
+  Finally, it may be possible 
+  to speed up our simulations
+  %MRS2: united atom would screw up the kinetics too much. 
+  %by reducing the number of atoms using united-atom representations
+  %of the liquid crystal monomers~\cite{horta_gromos-compatible_2016} or
+  by using hydrogen mass 
   repartitioning to allow us to increase the MD time step.~\cite{hopkins_long-time-step_2015}

### 2020-08-12 Ben_Manuscripts/hdphmm/response_to_reviewers.tex
Last changes before submission

@@
 
-    %BJC2: 
     We agree that a full comparison of our method to other methods for computing long timescale 
@@
     recent approaches we have developed within our research group.~\cite{coscia_capturing_2020}
-    %BJC2: added to make the point about our system being more complicated than those studied.
     It would be illuminating to test these methods on systems such as ours where there is
@@
     monoclinic unit cell with two dimensional order without in-depth testing.
-    % the grids that divide the homogeneous cubic unit cells of the referenced TEKMC studies to 
-    % our system which uses a monoclinic unit cell and has 2 dimensional order. 
-    %BJC2: maybe push back on the CS-DBP here? 
     Regarding the CS-DBP model, we are not convinced it would be suitable for our goals because
@@
     circumvents the need for relatively complicated methods used to identify binding sites 
-    by automatically identifying distinct dynamics characteristic of a class of bound states.
+    by automatically identifying distinct dynamics characteristic of classes of bound states.
 
@@
     where we used the mean squared displacement and the qualitative characteristics of the solute
-    time series in order to hypothesize transport mechanisms. In this work we "re-discover" these
+    time series in order to hypothesize transport mechanisms. In this work we ``re-discover" these
     mechanisms with minimal human intervention and characterize them in detail using the 
@@
 
-%MRS: additional thoughts:
-
-%1. Dynamic Bond Percolation theory (both the original version and the
-%chemically specific one) an and TEKMC are based on spatial clustering
-%and coarse-graining. Our approach is based on clustering and
-%coarse-graining the dynamics.  Can be more powerful, doesn't assume
-%(or minimally assumes - in some cases we assume pore vs. non-pore)
-%which configurations are important, which matters when there are a
-%diversity of different types of bound states, and diversity of
-%dynamics (in the pore, associated with the head groups, etc).
-
-%2. Dynamical behavior is more complex with our solutes than ion
-%interactions because of the richer range of interactions involved
-%(ionic binding PLUS hydrophobic binding, i.e. more types of bound
-%states; it's not just binding and hopping, and thus something
-
-%BJC2: I believe I had orginally addressed this briefly as well. Feel free to expand if you feel there is more to be said
-%3. Configurational behavior is more complex with the nanostructures,
-%because one cannot simply divide the structure into cubes
-%isotropically.  It may be easier to use our approach with more
-%diverse configurations, because we don't need to worry about
-%partitioning correctly.  This does push some of the difficulty into
-%choosing the coordinate system for the dynamics, but we have a lot
-%more freedom about choosing coordinate systems for the model than one
-%would using a uniform (or even nonuniform) partitioning of the
-%system. Yes, there are difficult choices to make but the model has
-%the freedom to make these choices.
-
-%4. One reason our simulations are longer because the timescales of
-%events observed generally are longer, and the number of solutes we
-%can put into the simulation is smaller (since the total pore volume
-%is smaller than it would be in an amorphous polymer).
-
-%5. We could probably construct our model it with a larger number of
-%more shorter simulations as well. Rare events require long timescale
-%sisulations.  However, the equilibration times for these simulations
-%(since we build from geometry, not from amorphous melts) are such
-%that we probably get more efficient use of simulations by running
-%fewer, longer simulations.
-
-% BJC2: assuming this comment about CS-DBP?
-    % MRS2: sorry, this was about OUR method, that it's definitely different because
-    % the clustering is not confiugurations based.
-%6. So it's not clear that this method is better than DBP or TEKMC
-% (especially since the results are a big ambiguous); one could define
-% bound states, and look at hops betwen then.  But it's definitely
-% DIFFERENT, it's not really the same thing at all, and we should push
-% back that it is similar.  We can argue that our approach is more
-% suited to our systems than the two configuration-based approaches -
-% one COULD try to use those approaches and they could be made to
-% work, but it's not a trivial thing to do, and we wanted to try
-% something where the data informed our model more completely and we
-% wouldn't have to try those modifications.
-
-    %r1_comment3
-    %BJC: not sure if I should ignore the JCTC part completely or basically just say what the editor said.
-    %MRS: my response below (Basically, saying what the editor said, in case it is send back out).
     \item \textit{Much of the writing seems more suitable for JCTC rather than JPC. I encourage the
@@
     Finally, we have added a figure with a picture of the system which we are studying 
-    (see~\ref{fig:membrane_side_profile}).
+    (see Figure~\ref{fig:membrane_side_profile}).
     \begin{figure}
@@
 
-    Author reply: We thank the reviewer for making this point. 
-    %BJC2: modded based on MRS suggestion    
-    In systems with less obstructions to motion, such as LLCs with a higher water content, most 
-    solutes and water will be relatively unimpeded, and diffusion constants can be obtained by 
-    standard techniques.    
+    Author reply: We thank the reviewer for making this point. In systems with less obstructions
+    to motion, such as LLCs with a higher water content, most solutes and water will be 
+    relatively unimpeded, and diffusion constants can be obtained by standard techniques.    
     However, we would still argue that our method would still be very useful for studying
-    solute dynamics in these higher water content systems 
-    %BJC2: incorporated MRS suggestion with small modifications    
-    by allowing one to study the dynamics of solutes that have longer residence times and interact
-    with moieties in a complex medium. %portions of the system away from the pore center.
+    solute dynamics in these higher water content systems by allowing one to study the dynamics 
+    of solutes that have longer residence times and interact with moieties in a complex medium. %portions of the system away from the pore center.
     %Interactions characterized by different dynamical behavior even on short time scales can
     %still be highly informative. 
-    This is the basis for the point we make in the introduction:``. . . direct calculations of diffusion 
-    constants may obscure the molecular mechanisms controlling transport". Therefore we would
-    prefer not to limit the range of application of this method. 
+    This is the basis for the point we make in the introduction:``. . . direct calculations 
+    of diffusion constants may obscure the molecular mechanisms controlling transport". Therefore
+    we would prefer not to limit the range of application of this method. 
     %BJC2: added    
@@
     selectivity. \hl{In many systems, including LLC membranes with water contents higher
-    than the 10 wt\% water system studied here, making this connection can be relatively 
+    than the 10 wt\% water system studied here, making this connection can be a relatively 
     straightforward calculation with standard techniques since small solutes and water 
@@
 
-    Author reply: 
-    %We thank the reviewer for posing this question as this a constraint to which 
-    %we gave thought but neglected to emphasize in the main text. 
-    %BJC: he's not saying that solutes should stay in the aqueous pore region right? We talk pretty
-    % extensively about solute behavior in the tails so his steric argument is confusing me.
-
-    %MRS: It is a little confusing. First, we never use the term "pore
-    %radius", since the structure of the pore makes it very hard to
-    %define a single pore radius.  The term "pore region" is used once
-    %(about line 995), that that should probably be "pore center".
-    %BJC2: changed pore region to pore center
-    %Second, it's not clear what is meant when they say it's not clear
-    %how they are constrained when they must be by steric
-    %interactions.  Since steric interactions do NOT keep them in the
-    %pore region (at least for the smallest solutes).  Figure 2 is a selection of a trajectory.
-
-    %    First, we would like to clarify
-%    that our simulations suggest that small solutes can partition out of the pores and into
-%    the dense tail region. This is not a particularly favorable move as evidenced by our radial
-%    distribution functions, but it does happen and could conceivably lead to rare jumps of solutes
-%    between pores (although we have not observed any).
-
-    %MRS: how about this?  
-    %BJC2: seems good. made some minor edits
-    We are grateful for the opportunity to clarify some of the details of the simulation 
-    geometries. We avoid defining a ``pore radius'' because the radial distribution of 
+    Author reply: We are grateful for the opportunity to clarify some of the details of the
+    simulation geometries. We avoid defining a ``pore radius'' because the radial distribution of 
     head groups and even tail groups is spread over several nanometers and we have
@@
     the pores.~\cite{coscia_understanding_2019,coscia_chemically_2019} 
-%    This partitioning occurs to the extent that smaller molecules like water and methanol
-%    can in fact move between pores in rare instances.
-    %BJC2: I don't think I've actually published anything stating or proving the above. 
-    %I think it's particularly hard to get by the crosslinks. But I do believe it could happen.
-    %rephrased with that in mind.
     Therefore, it may be possible that, in rare instances, smaller molecules like water and
@@
     quantity due to the hexagonally packed pore configuration).
-    %MRS: though I'm not QUITE sure that's right, since the hexagonal packing means that the transition between pores
-    %occurs at different distances depending on the angle. 
-    %BJC: Yeah, I know what you mean. I added the bit in parentheses above to acknowledge that.
     Each time a state change occurs, the mean position of the solute in the $r$ dimension 
@@
 
-    %BJC: figured I'd get your feedback on above before writing the part that will go into the text.
-
     %r1_comment6
@@
     by the figure rather the process of generating the figure. However, we believe that the 
-    only real offender among our captions was Figure 8. Therefore we have modified the language
+    only real offender among our captions was Figure 8 (now Figure 9). Therefore we have modified the language
     of that figure:
@@
     of the monomer, color coded to match (a). (c) The 95th percentile of hydrogen bond lifetimes for
-    each type of hydrogen bond in each predominant state, the 95th percentile of hydrogen bond lifetimes
-    (d) The frequency and lifetimes of solute association with sodium ions. Methanol associates with sodium
-    less than 10\% of the total time it occupies any of the predominant states.    
+    each type of hydrogen bond in each predominant state (d) The frequency and lifetimes of solute 
+    association with sodium ions. Methanol associates with sodium less than 10\% of the total time 
+    it occupies any of the predominant states.    
     \end{quote}
@@
 
-    % BJC2: shifted initial focus towards mechnistic understanding. Still kept part about speeding up simulations
-    % as I think it's worth discussing ways to make this an actual high throughput technique. 
     Author reply: We thank the reviewer for pushing us to further evaluate the practicality of our
     method as a tool for experimentalists. The length of our simulations in this paper are indeed 
-    quite long. 
-    %The dynamics of the solutes are somewhat slow and we wanted to ensure we gathered
-    %enough data for a sufficient parameterization. 
-    However, the length of the simulations primarily influences the reliability of the long
+    quite long. However, the length of the simulations primarily influences the reliability of the long
     timescale predictions of our model. We believe one of our method's greatest strengths is its 
@@
     \begin{quote}
-    In consideration of our ultimate goal, which is to use high-throughput simulations to 
-    facilitate our understanding of LLC membrane design for solute-specific separations, the size 
-    of our system and length of the accompanying molecular simulations appears to be somewhat 
-    impractical. Dependent on one's goals, it may not be necessary to run such long simulations in order 
-    to extract valuable mechanistic insight. We originally uncovered the mechanisms discussed
-    in this study using trajectories a fraction of the length here.\cite{coscia_chemically_2019} A 
+  Given our ultimate goal, to use high-throughput simulations to facilitate our understanding 
+  of LLC membrane design for solute-specific separations, the size of our system and length 
+  of the accompanying molecular simulations may be somewhat impractical. In many 
+  situations, it may not be necessary to run such long simulations in order to extract 
+  valuable mechanistic insight. We originally uncovered the mechanisms discussed in this
+  study using trajectories a fraction of the length here~\cite{coscia_chemically_2019}. A 
   strong mechanistic understanding of solute transport with respect to the chemical features of a 
   given LLC monomer may be enough for experimentalists to eliminate entire subsets of potential
-    design changes. However, it may still be valuable to consider how one might make these simulations
-    amenable to high-throughput studies. We would like to emphasize that our large, fully atomistic 
-    models will be extremely valuable as a benchmark system used to explore less expensive models. 
+  design changes. However, it is still valuable to consider how one might make these simulations
+  amenable to high-throughput studies. We emphasize that our large, fully atomistic 
+  model will be extremely valuable as a benchmark system used to explore less expensive models. 
   For example, we could explore systems built with fewer LLC monomers by making the membrane pores
@@
   data that must be discarded. Alternatively, we could use grand canonical Monte Carlo simulations
-    to load solutes into the membrane~\cite{snurr_prediction_1993}. Finally, it may be possible 
-    to speed up our simulations by reducing the number of atoms using united-atom representations
-    of the liquid crystal monomers~\cite{horta_gromos-compatible_2016} or by using hydrogen mass 
+  to load solutes into the membrane~\cite{snurr_prediction_1993}. If simulation resources are
+  available, the simulations could be split up into larger numbers of shorter simulations.
+  Finally, it may be possible to speed up our simulations by using hydrogen mass 
   repartitioning to allow us to increase the MD time step.~\cite{hopkins_long-time-step_2015}
@@
 
-    %BJC: This is copied straight from the reviewer response for the previous paper.
-    %BJC2: do you think I should reword this at all to make it different?
     Author reply: The reviewer makes a valid point. This work started in parallel with experimental
@@
     First, we added additional clarification before describing the bootstrapping procedure (added text
-    is highlighted in red):
+    is highlighted in yellow):
     \begin{quote}
-    Our bootstrapping procedure varied dependent on the method of trajectory generation. \textcolor{red}{
+    Our bootstrapping procedure varied dependent on the method of trajectory generation. \hl{
     The following procedures correspond to the methods described above:}

### 2020-08-12 Ben_Manuscripts/hdphmm/Draft.tex
Last changes before submission

@@
   In many systems, including LLC membranes with water contents higher than the 10 wt\% 
-  water system studied here, making this connection can be relatively straightforward 
+  water system studied here, making this connection can be a relatively straightforward 
   calculation with standard techniques since small solutes and water can move relatively
@@
   stochastic trajectories that reach the diffusive regime~\cite{neyertz_trajectory-extending_2010}
-  It is possible to parameterize TEKMC models with relatively short simulation trajectories 
-  which facilitates systematic studies of small perturbations to material constituents.~\cite{hanson_computer_2012}
+  If the dynamics of the system are fast enough, it is possible to parameterize TEKMC models with
+  relatively short simulation trajectories which facilitates systematic studies of small perturbations
+  to material constituents.~\cite{hanson_computer_2012}
   In a related approach, dynamic bond percolation (DBP) theory can be used to quantify the
@@
 
-  Given our ultimate goal, to use high-throughput simulations to 
-  facilitate our understanding of LLC membrane design for solute-specific separations, the size 
-  of our system and length of the accompanying molecular simulations appears may be somewhat 
-  impractical. In many situations, it may not be necessary to run such long simulations in order 
-  to extract valuable mechanistic insight. We originally uncovered the mechanisms discussed
-  in this study using trajectories a fraction of the length here~\cite{coscia_chemically_2019}. A 
+  Given our ultimate goal, to use high-throughput simulations to facilitate our understanding 
+  of LLC membrane design for solute-specific separations, the size of our system and length 
+  of the accompanying molecular simulations may be somewhat impractical. In many 
+  situations, it may not be necessary to run such long simulations in order to extract 
+  valuable mechanistic insight. We originally uncovered the mechanisms discussed in this
+  study using trajectories a fraction of the length here~\cite{coscia_chemically_2019}. A 
   strong mechanistic understanding of solute transport with respect to the chemical features of a 
@@
   amenable to high-throughput studies. We emphasize that our large, fully atomistic 
-  models will be extremely valuable as a benchmark system used to explore less expensive models. 
+  model will be extremely valuable as a benchmark system used to explore less expensive models. 
   For example, we could explore systems built with fewer LLC monomers by making the membrane pores
@@
   data that must be discarded. Alternatively, we could use grand canonical Monte Carlo simulations
-  to load solutes into the membrane~\cite{snurr_prediction_1993}.
-  If simulation resources are available, the simulations could be split up into larger numbers of shorter simulations.
-  Finally, it may be possible 
-  to speed up our simulations
-  %MRS2: united atom would screw up the kinetics too much. 
-  %by reducing the number of atoms using united-atom representations
-  %of the liquid crystal monomers~\cite{horta_gromos-compatible_2016} or
-  by using hydrogen mass 
+  to load solutes into the membrane~\cite{snurr_prediction_1993}. If simulation resources are
+  available, the simulations could be split up into larger numbers of shorter simulations.
+  Finally, it may be possible to speed up our simulations by using hydrogen mass 
   repartitioning to allow us to increase the MD time step.~\cite{hopkins_long-time-step_2015}
@@
   \end{subfigure}
-  %y-axis label being cut off?
-  \caption{(a) We analyzed hydrogen bonds donated by methanol to the highlighted oxygen
-  atoms in three regions of the monomer: the carboxylate groups (blue), the ether linkages
-  (green) and the tails (red). (b) For each predominant state (states 1--5 described in 
-  Figure~\ref{fig:prevalence}), we plotted the fraction of the total time in that state 
-  spent hydrogen bonding to various regions of the monomer, color coded to match (a).
-  (c) For each type of hydrogen bond in each predominant state, we calculated the 95th percentile
-  of hydrogen bond lifetimes. (d) We also analyzed the frequency and lifetimes of solute 
-  association with sodium ions. Methanol associates with sodium less than 10\% of the total 
-  time it occupies any of the predominant states.
+  \caption{(a) Hydrogen bonds can be donated by methanol to the highlighted oxygen atoms in three 
+    regions of the monomer: the carboxylate groups (blue), the ether linkages (green) and the
+    tails (red). (b) For each predominant state (states 1--5 described in Figure~\ref{M-fig:prevalence}),
+    the fraction of the total time in that state spent hydrogen bonding to various regions
+    of the monomer, color coded to match (a). (c) The 95th percentile of hydrogen bond lifetimes for
+    each type of hydrogen bond in each predominant state (d) The frequency and lifetimes of solute 
+    association with sodium ions. Methanol associates with sodium less than 10\% of the total time 
+    it occupies any of the predominant states.   
   }
